\chapter{A Day In The Life Of A Second-Year Martial Artist (3)}

Although the youngest of the Virtuous Quartet of Qinghe was eliminated, making them the Virtuous Trio instead, it was still a fight of three against one. Traditionally, having such a difference in numbers was a standard advantage, and it was indeed the case here.

The difference stemmed from their attitudes.

Ahn Seongil was overwhelmed by the numbers and looked for a way to escape out of fear, while the Virtuous Trio of Qinghe pressed for a quick decisive battle.

The importance of momentum in a fight could not be overstated. This was clearly exemplified by Ahn Seongil, who was constantly retreating and busy fending off attacks, and the purely offensive Virtuous Trio of Qinghe.

This went on for about twenty strokes. The modern-day equivalent of a stroke in Wulin was a turn in a turn-based strategy game.

Ahn Seongil thought.

\textit{Huh. This isnt as hard as I thought?}

The Eldest Brother of the Qinghe Trio, Jo Gaksan, thought.

\textit{Damn it, was the gap of the wall between us this severe?! }

Truth be told, the ultimate method of joint attack was not three against one, but four against one. 

Humans had four cardinal directions North, South, East, and West so true mastery of joint attack was controlling all four. 

This concept had long been proven.

In Buddhism, there were the Four Heavenly Kings, and in Daoism, there were the Four Auspicious Beasts, illustrating the ancient wisdom of dividing the points of the compass into four.

Therefore, three was an incomplete number.

Moreover, the opponent was one of a superior realm.

The difference between a Late-Stage First-Rate and an Early-Stage Peak Realm was just one step, but it was a higher wall than one might think.

Another ten strokes passed. 

Jo Gaksan exchanged glances with his brothers, a conversation carried out solely with their eyes built from years of brotherhood.

'This wont do. Lets get out of here. We have to take the youngest with us as well.'

'Good idea, Eldest Brother.'

'I was waiting for you to say that, Eldest Brother.'

The contents were more disheartening than expected. But considering Jo Gaksans moniker as the Eldest Brother of the Virtuous Trio of Qinghe, it only stood to reason that he would decide so.

In Wulin, monikers were a far simpler principle than one might think.

Those in the First-Rate were respectable martial artists, but there were far too many of the same realm in the current Wulin.

Therefore, to earn a splendid moniker as a First-Rate Expert, one must perform feats that everyone would acknowledge and admire.

But as there were many people and few heroic deeds, monikers usually combined the place of activity, a characteristic, and a tendency.

(Active in) Zhengyou, Ugly (In actions), Devil (Bad guy)

(Active in) Qinghe, Gale (Fast), Virtue (Good guy)

Hence, Jo Gaksan, the Virtuous Gale of Qinghe, was known for his storm-like speed; especially, his strategy to retreat like a passing gale when the fight turned unfavorable!

It was a moniker given by people who admired that quality of his.     

'But seeing how the youngest isnt showing up, he must have broken something.'

'The youngest always slips away, after all. The Third will take care of him.'

'Wait, me again? Can't Second Brother take care of him this time?'

'Oho? The Third is talking back?!'

Unfortunately, the youngest was already dead. But the news of the youngest death had not reached them yet because dead men tell no tales.

If only the youngest had said, 'I'm dead, Brothers', then the trio, furious over his demise, would have fought to their last breath and might have managed to take down the villain; the murderer of their youngest.

However, the only thought they currently had was escaping.

Jo Gaksan barely parried Ahn Seongils sword strike and suddenly shouted.

"Now! Yeonhaeng-gwisan!"

Ahn Seongil paused his attack and retreated quickly. 

He did not know what Yeonhaeng-gwisan meant, but he sensed it could be a dangerous technique.

However, Yeonhaeng-gwisan meant nothing. 

It was just a random word Jo Gaksan shouted to scare his opponent, so that he could exit like a gale. 

It was a similar case to how the dead Zhuge Liang defeated the living Sima Yi with meaningless words. 

With that, he succeeded in fending off a Peak Realm Master.

It was truly a miraculous strategy. 

And so, the famed Virtuous Gale displayed the brilliance of his moniker. 

The three individuals swiftly distanced themselves like a tempest! 

Ahn Seongil was left blinking in dumbfoundedness.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When A-Qing went upstairs, she saw three people running towards her like lightning.

She scanned the numbers above the three peoples heads: their Karma.

Seventeen, Nine, One.

Although the numbers were low, they still held Righteous Karma.

They seemed like good guys, so they were probably not the Ugly Devil of Zhengyou.

A-Qing quickly lost interest, but the three people flinched as they passed by her.

It was because her appearance was far from ordinary.

After all, anyone would startle at least once when seeing a female swordsman smiling with blood on her.

Moreover, she exuded a suffocating aura, as if there was a pressure constricting their very hearts; perhaps it was because of her eyes, turned feral, harbored a sinister hue.

But A-Qing did not make eye contact with the Virtuous Trio of Qinghe.

This was a nonverbal expression among martial artists.

In essence it meant that they had no business with each other, so they should go their separate ways.

After the three people passed by, A-Qing immediately identified the villain on the upper floor of the inn.

There was someone with an unusually high number above their head.

The villain had Three Hundred Seventy Six Points of Evil Karma, a person who had accumulated a terribly large amount of evil deeds.

In other words, he was a bastard who could be killed. 

Killing him would actually be a service to the world, for he was such trash.

When A-Qing made eye contact with Ahn Seongil, he rolled his eyes upwards to avoid her gaze.

It was the same nonverbal expression among martial arts.

'Let's go our separate ways.'

Ahn Seongil did not want to get entangled in this situation with A-Qing.

Wasn't there an old saying in Wulin?

Be wary of children, women, and the elderly.

Of course, this saying didn't mean to be especially wary of such a demographic.

After all, if children, women, and the elderly were excluded, the only ones left were adult men.

And everyone would become cautious and wary when facing adult men.

The saying 'Be wary of children, women, and the elderly' meant to be cautious and not let your guard down around anyone you meet in Wulin.

Ahn Seongil wanted to avoid conflict because of this very wisdom, but A-Qing had business with him.

"Hey. You there. Fucking old fart. Are you that piece of shit human scum called the Ugly Devil of Zhengyou?"

It was an unexpected verbal assault, completely out of the blue.

Ahn Seongil wore a dumbfounded expression.

It was a curse so severe that it made him doubt his ears.

"Yeah, you, old fart. Who else here has son of a bitch fucking written all over their face besides you?"

Ahn Seongils face turned beet red.

It was natural, considering he was being cursed by someone significantly younger; perhaps younger than what his daughter or even granddaughter would be.

"How dare this bitch who is still wet behind the ears-"

"What? What bitch? Did you just swear at me? How dare you curse at me so severely. That is insulting. I can't hold back."

For someone who couldn't hold back, she was grinning from ear to ear as she drew her sword when-

"This crazy gir! Heup."

Ahn Seongil hastily closed his mouth.

It was because of the Qi emanating from A-Qings sword, unwinding like threads. 

This phenomenon, where Qi overflowed even after Sword Qi was channeled, was called Sword Threads.

It was a technique used by martial artists of the Late-Stage Peak Realm.

Ahn Seongil broke out in a cold sweat.

The girl in front of him was a Master whose realm was much higher than his.

He was facing a life-threatening crisis.

An overwhelming difference in skill!

"Crazy? You're swearing at me again? Wow, that's so insulting. Ha, I'm getting angry, so very angry."

"No, that's not what I meant."

"If you had insulted my clan, my parents, I might have held back. But insulting me? I can't tolerate that. There is no more need for words! Die! My Moonlight Sword is starving! "

Despite her playful movements, the tip of the womans sword split into three shapes before one could even take a breath.

The Sword Qi surged in three forks.

Ahn Seongil's brain was overheating fiercely.

What was the real movement and what was the fake? 

To live or to die. There was no time to ponder.

It was the moment Ahn Seongil was about to gamble his life in front of this deadly trilemma.

A sensation like the hair on his entire body was standing on end!

All three are real movements! 

In a moment, he realized all three were real sword movements. This was the extra sensory perception one had when their life hung by a thread, also referred to the culmination of his efforts of the upper dantian in martial studies.

Ahn Seongil managed to deflect the sword strike targeting his heart and twisted his body with all his might. His shoulder and waist felt icy cold, followed by intense pain. 

He had managed to fend off only one attack.

There were already two injuries.

The disparity in skill was despairing.

Not only was there a gap between the Early and Late-Stages of the Peak Realm, but the womans Sword Art itself was in a superior realm.

Considering the young womans skill at such an age, her background must be from an extraordinary sect.

Meaning, even if he lost, he would die, and even if he won, death would find him through the hands of pursuers.

Thus, there was only one answer.

He must not fight; it was a battle destined for doom.

"Wait! Great Expert! It's a misunderstanding! A misunderstanding!"

"A misunderstanding my ass. I heard you clearly. You insulted me. You shall pay for this humiliation with your life!"

"No, No! It isnt like that! Great Expert, wa-wait!"

"Great Expert? Do I look that old to you? How dare you one-sidedly raise a womans age like that."

"Y-Young Expert, please wait!"

"Young Expert? An inferior like you who had just reached the Peak Realm dares to address a martial senior like that? How dare you! "

"Female Expert! Please, Female Expert! Hear me out just for a moment!"

"Female Expert? Is there a separate title for male and female Experts? Gender discrimination is muddling the world, thus here in this place, I shall break such chains."

The womans sword continued to fly at him relentlessly.

Sometimes in three forks, sometimes four, and when it reached five forks, he lost the will to counter.

He could do nothing but blabber desperately.

It had already been twenty or so strokes.

It was a miracle of itself for him to stay standing.

Then, as if it was all a lie, the assault stopped.

"I'm telling you this because you keep saying it's a misunderstanding."

"Yes, Great Expert, no, Young, no that."

"I was just about to enjoy an expensive meal that I managed to buy with great difficulty, you see. It was a very special anniversary to me. The happiest moment I had since starting my Wulin journey."

"Um, uh. I apologize for causing a distu-"

"No, what? Do you think I'm some murderer who would kill someone just because they're noisy? That's not it. Something fell from the sky, you see. Since were inside an inn, it must have been the ceiling, right?"

A-Qing turned her head.

Ahn Seongil followed her gaze and turned his head too.

A gaping hole in the floor was visible.

Ahn Seongil started sweating bullets.

\textit{So that was why there was blood all over her.}

"Very well then. Now, you understand why youre going to die, right?"

"P-Please spare me!"

"Hm. What should I do."

A-Qing pretended to think for a while, dragging out the silence, before speaking.

"First, hand over your money. Since you ruined my meal. And you also ruined my clothes."

"I-I will give it to you!"

"Ah, how am I supposed to hold back from this? So harsh."

"What? What?"

"Again! Give me your money!"

"I will give it to you!"

"I don't need it!"

Ahn Seongil was flustered.

What the fuck did she want him to do then?

Was she toying with him after pulling him down to his kn-

\textit{Ah.}

Ahn Seongils eyes turned rotten.

The reason he was still alive and able to withstand the attacks was that even when the sword strikes flew at him at once, there was always only one killing move aimed at a vital spot.

It was so that he could somehow block and parry the rest with his body if he dodged the killing move.

In other words, the woman was toying with him.

With a frivolous grin on her face, like a cat playing with a bird.

\textit{I-I've been caught by a fiend, a slaughterer.}

"Ah. You got me. Oops?"

A-Qings smile deepened.

"That's why you should've lived virtuously. This is all karma, okay? Karma. It's because my Moonlight Sword thirsts only for the blood of evil."

A-Qing raised her sword.

Sensing the end, the villain roared.

"Do you think you'll be safe, you bitch! Yes, I'm a bad person! But do you think a bitch like you isnt?! I'll be waiting for you in hell!"

"Hell my ass. Do you even know how high my Righteous Karma is?"

Ahn Seongil's world spun.

His collapsing body came into view.

As he was dying, he thought.

\textit{But how could a sword falling straight down cut the neck?}

\textit{What kind of miraculous swordsmanship was this.}