\chapter{A Day In The Life Of A Second-Year Martial Artist (1)}

A-Qing was currently an inhabitant of Wulin, as well as a former member of the modern age.

This fact brought a significant enlightenment to A-Qing. 

The life of a once single, production worker of the modern era meant that work and people were sometimes (often) shitty. As such, this led to ones well-being deteriorating, as they endured the hardship of not being able to sleep when desired, constantly rubbing at exhausted eyes.

However, there were no problems when it came to just living.

Modern civilization meant that even when one lived alone, basic needs were manageable and they could survive without particularly feeling any life-threatening dangers.

But what about the world of Wulin, these primitive ancient times of China?

If one did not have power nor money, they would just die. There was no other option.

So, over the past year, A-Qing's time here was a continuous, solemn struggle to preserve her very life.

At least the people of Korea didnt draw knives and attack just because they made eye contact or killed one another over a shoulder bump in a sword duel.

It was almost impossible for a modern person with a fragile spirit to survive in such a barbaric civilization.

Yet A-Qing was still alive and breathing.

Of course, she was fortunate in many ways.

Firstly, A-Qings body was robust.

In modern terms, he had followed a guide when creating a character, focusing on a build that went all-in on strength and stamina to get through the Early-Game. 

And when A-Qing opened her eyes, she found herself in the body of the character she had created.

She was stronger than most men and her steel-like body hardly tired.

And most importantly, the choice of Constitution was perfect.

A-Qings Constitution, Blood Poison, neutralized all poisons that existed in the narrative.

Even food poisoning was considered a poison, so she could eat anything without falling ill.

She could seriously eat anything without worries.

And so, A-Qing survived.

Since she could not even make eye contact with Third-Rate Unorthodox thugs, she fought over discarded food with beggars. As stealing potatoes and radishes was not easy, she was beaten by farmers.

Like that, she endured a year.

And now, she had become a proper martial artist in her second year at Zhongyuan. 

In her own way, it was a special commemoration for A-Qing as well. 

Thats right, I too am a proper martial artist, now in my second year. I should try to live more like a martial artistMore like a human.

Even just now, she had brought in the head of a wanted villain to the administrative office and received the bounty.

She still vividly remembered the first time she killed someone in her first year here, crying and vomiting, but now she could cut through arms and necks without hesitation.

\textit{At this rate, I am also turning into a splendid Wulin gangster. Mmm. Nice.}

A-Qings majestic chest swelled.

It was the pride of a Jianghu newbie, just a little over a year of life in Zhongyuan.

Even if it wasn't A-Qing, about a year after one embarked on this martial path tended to be the time when confidence was at its peak.

Of course, it wasn't clear to A-Qing herself if she had really entered her second year.

After all, she didn't mark the days like a castaway on a deserted island or a kidnapping victim secluded in a dark room.

But she had fallen into this world in the warm spring, survived the winter, and now the weather was warming up again.

As such, it was roughly the 1st anniversary.

Humiliating days flashed through her mind.        

When she woke up naked in a completely unknown world, there was almost nothing A-Qing could do.

After all, did money grow on trees?

Or, like in a game, could she break into houses, shatter some jars, open boxes, and boldly steal in front of the homeowner?

Of course, if there was no owner, it was possible, and there were actually professionals who specialized in this.

However, burglary required more sophisticated skills than she thought, even if it was an empty house.

If she had known she would end up like this, she wouldn't have worked as a production worker but as a burglar instead.

Fortunately, there was one part that was the same as a game.

It was that killing people gave money.

In Zhongyuan, people carried pouches called moneybags to hold their assets.

If the owner disappeared, the person who picked it up would become the next owner, so if you killed someone, you could rightfully inherit their moneybag.

Even so, A-Qing was always poor.

It was because she was not a murderous robber aiming for money.

If she had to kill, she killed only rotten bastards.

Sometimes, when she brought their heads to the office, she received a bounty, albeit rarely. But the amount earned was not that much either.

As soon as one left their nest and had to become a responsible adult, every little thing cost money.

To exaggerate a bit, even breathing costs money.

As such, life obviously couldn't help but be miserable.

But today, lets break free from being miserable.

It was a day she could celebrate with pride.

It was the 1st anniversary!

"Over here, Server."

At A-Qing's call, the server rushed in.

There was a mole as big as a housefly beside his nose.

It was clear that this inn was not any ordinary inn.

After all, the mole on the servers face was a sign of fortune.

The bigger and clearer the mole, the higher the server's fee. One could tell the status of the inn by the server's mole.

"What's good here?"

"Theres nothing we can't cook, but the dish I recommend today is chicken steamed with ginger and then fried with dark soy sauce and oil. Today is the day the chickens came in from the cockfighting arena, so the flavor is extraordinary."

The server skillfully recommended a dish.

Starting at the age of fourteen and soon reaching his 30th anniversary here, the experienced server could immediately gauge the customer.

As she was wearing light robes with traces of Qi here and there, she must be a poor female swordsman of Wulin. Though there were dark circles under her eyes, her expression was not one of exhaustion.

As such, it must be a customer who had something good happen, wishing to celebrate, and preferred a generous and oily dish over a small portion due to her poor attire.

Cockfighting arena and whatnot was purely bullshit.

In fact, the server did not know much about it either.

However, it was just a chicken dish, not even a duck.

This level of lip service was needed to satisfy the customer as well.

A-Qing, the second-year newbie of Wulin lifestyle, had no idea what the server was thinking.

She was just happy. 

\textit{Chicken!}

\textit{Fried chicken!}

\textit{The soul food of Koreans!}

"Are you in need of alcohol as well?"

"Yes! One strong bottle of hard liquor!"

"Then how about Bi Hongju. It is from the Bi Family's Brewery behind here. Although this is only their first generation, it is known for its extraordinary potency. Even the elderly of the Beggars Union praise it."

If it was only a first-generation brewery, it couldn't boast of making good liquor.

Moreover, the talk about the elderly of the Beggars Union was purely a scam.

How could beggars truly know the subtle tastes of liquor? They would just down it, after all.

In the end, it was all just talk.

But how that talk was packaged could please the customer.

The server was a high-class personnel and practically an artist in hospitality.

"One fish-scented sweet and sour chicken here! One Bi Hongju!"

The server shouted the order as he walked away.

Shouting the order wasn't to inform the kitchen. Nor was it to double-check with the customer.

It was to let the other clients in the inn know what this person ordered.

The more expensive the order, the louder the voice, and occasionally, when a really big customer came, they even went out to the main road to yell the order out.

However, A-Qing's order was not loud enough for the server to raise his voice. It was simply because the server had clearly seen and read into A-Qing's heart.

After all, it was obvious what a poor customer would expect.

Unaware of this consideration, A-Qing was all smiles.

The other customers in the inn who saw A-Qing also let out a smirk, as soon after, they had roughly realized what kind of situation this was.

A-Qing was the only one unaware.

A-Qing. A whopping two years spent in Wulin.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the previous era, there was a song that a legendary band of chivalrous individuals (basically, akin to thieves) loved to sing.

The first verse was incomparably unique.

'Heroes do not bother studying'.

But the era of ignorant and unsophisticated sword swings had passed and in this new era, martial arts also became a branch of study.

The higher the level of martial arts, the more it entwined with the principles of the world.

In fact, without contemplating the Dao and ideology, one could not become a peerless Master.

However, the zenith of the era before the last, the Greatest Under Heaven, loved this song.

His title was the Celestial Martial Emperor.

It was a terrifying moniker. 

Even if he was the Greatest Under Heaven, how could he dare to impersonate the title of Emperor!? 

It was akin to challenging the Jade Emperor to a showdown.

So, they actually did fight.

As the stern Jade Emperor never avoided a challenge, a mere word of conspiracy would gather the military forces of all that was under Heaven.

And the result?

The Celestial Martial Emperor was truly fitting of his title.

If the Celestial Martial Emperor had been defeated, he would have been nicknamed something like The Small Fry Who Stood Against Heaven or Traitor to Heaven.

It was a famous tale that the Celestial Martial Emperor suppressed thirty thousand soldiers, grabbed the Emperor by the collar, climbed to the top of the Imperial Palace, and sang a revised version of his favorite song.

\begin{quotation}
	Heroes do not mind the gazes of others.
	
	What does it matter when All Under Heaven is beneath me
	
	Even if my status is humble
	
	Who dares to hinder my path
\end{quotation}

Thus, the Celestial Martial Emperor succeeded in redefining the relationship between the authorities and the martial world, creating a new law that the two should ignore each other and mind their own business.

With that, the Celestial Martial Emperor ascended as the godfather of all martial artists.

Afterward, the Celestial Martial Emperor literally realized the legend of ascending to Heaven as a Daoist Immortal, leaving a legacy as an imperishable icon.

The musical achievement of composing the most beloved song of that eras martial artists was just a bonus. 

Truly the very definition of a man who shaped an era!

However, there were side effects.

Some people misunderstood the lyrics of the song Heroes do not mind the gazes of others.

If heroes did not mind the gazes of others, did it mean that those who were not heroes should mind them?

Then, bastards who were cautious of others weren't heroes, right? 

The ascended Celestial Martial Emperor would have lamented up above Heaven, pounding his chest in frustration.

And as a result, here in this place

The Virtuous Gale of Qinghe, Jo Gaksan, thought of himself as a hero. 

Jo Gaksan was dining with his sworn brothers.

Together, with the three of them, they were known as the Virtuous Quartet of Qinghe and had a fair amount of pride in their renown.

Then he suddenly recognized a face.

The Ugly Devil of Zhengyou, Ahn Sung-il.

Despite his title, his looks were quite decent.

However, the nickname Ugly Devil of Zhengyou was not for his face but for his extremely vile and dirty deeds.

His main business was human trafficking, and besides that, he was a son of a bitch who committed all kinds of evil deeds such as theft, robbery, murder, rape, arson, and fraud.

Heroes must immediately punish evil without any tolerance.

Of course, only if the evil was weaker than them!

Ahn Sung-ils level was known to be in the early stages of the Peak Realm and Jo Gaksan was merely in the late stages of a First-Rate martial artist.

However, they were sworn brothers for such times. If not, what other reason would there be to uncomfortably move around in a group of four?

One against four.

Each individual of the Virtuous Quartet of Qinghe might be weaker than Ahn Sung-il, but together, we were strong.

Because that was what we are!

Indeed, they couldn't just stand by and watch evil get away!

Jo Gaksan finally made up his mind after calculating the odds from various angles.

Heroes do not mind the gazes of others.

The act of minding others gazes included causing a disturbance in a crowded inn during dinner time, potentially causing direct or indirect damage to those around.

Such minor collateral damage was trivial in the face of a grand cause that was executing justice and eliminating evil.

The Virtuous Quartet of Qinghe quietly exchanged glances.

Jo Gaksan tapped the table three times.