\chapter{Chaotic Mess (5)}

'I'm going to kill that kid who bought that net.'

It was the thought of Ambassador Jangpyeongmun Toungung.

The sword is basically a cutting weapon.

The handle is long and easy to handle, and the weapon itself has great power even when you simply apply your body weight to it and swing it down.

This is also the reason why the Sapas love to use it, because it is the fastest way to become stronger by adding Tao to the basic strength and speed of the unmanned unit.

The martial art of Taoism itself is very simple and easy to learn.

The secrets of Kwaina Hwan were advanced techniques that can only be found in high-level Taoist techniques.

There is only one blade, so just swing it and you're done.

The tip is sharp so it can stab you.

But that's possible because the center of gravity is towards the tip of the sword, and the sword gradually gets thicker from the handle to the tip. In the first place, it doesn't stick well after stabbing.

Of course, there is a sword called the Leaf Sword, which is specialized for the ever-changing atolls with a fluttering blade.

There were also types called yedos or hwandos, which have thin and light blades and can be used like swords to cut, stab, and so on.

But it is not in the long commentary.

Isn't this a school of men who use weapons that were truly men's weapons, such as thick swords, daedo, and gamsando, that were large, thick, sharp, and forcefully pushed forward to cut and strike?

But that damn six-hour net!

Toungung ground his teeth.

Now it was the Cheonhwageom that was openly showing off its body.

Several blades strike down his shoulder, but he is stopped by a net made of wire and rope, about two fingers thick.

A loud scream of "Ugh!" erupts.

But originally, when it really hurts, you make a gasping sound like "Ah, ah," and a high-pitched scream like "Kkaek, kaek" means that you can endure it.

No matter how hard you swing your sword, it's blocked by the rope and has no effect beyond just hitting you.

Even if you shout to stab, there is no stabbing technique in the first place in the Jangpyeongmun's plain sword technique, so you just stab clumsily and awkwardly without putting any weight on it.

So, although the tip is sharp, it ends up getting stuck in the thickest part of the blade and making a puncture wound.

The red circles dotted on the white uniform were proof of this.

So it's not like the blade doesn't go in.

The problem was that Toungung's weapon was a glans sword.

A glissando is a weapon with a heavy decoration attached to the end of a long sword. It is usually called a glissando because it is shaped like a ghost's head.

If there is a weight on the tip of the sword, how much cutting power will it have?

But? There is no tip, so I can't stab.

The blade of the Thousand Flower Sword flashes.

It is a massive, heavy weapon that is too big and heavy to be called a sword, and it is hard to believe how one can swing it with one hand.

The steel on it looks like it's an inch thick, showing how foolishly they're betting.

One of his great disciples is cut diagonally by him.

He was a promising young man from a sect that was at its peak.

He tried to block it by raising his sword, but was repelled and bounced away helplessly. The blade of the Cheonhwageom, imbued with a powerful energy, dug into his ear and came out under his armpit.

No matter how strong you are, you can't just stand up straight after a powerful blow that cuts through a person like that.

The tip of the Cheonhwageom sword that cut the great disciple was buried deep in the ground, and he was in a crouching position with his back bent and his fist almost touching the ground.

In contrast to the wide front, the blades flow down the narrow and slender back.

The crown of the Toungung Palace also falls in a wide curve with the most brilliant starlight.

As a woman in a state of depression, I looked straight towards the graceful yet obscene and lewd curve of her spine beyond her uniform.

A powerful blow that should have broken the spine, but the feeling of being blocked firmly by the net.

Ugh! Cheonhwageom fell to the ground with a thud, but soon got up on all fours and stood on his own two feet while letting out a groan.

Even if the blade was blocked by the net, if he struck down with all his might, it should have shattered as if struck by a sledgehammer, but Cheonhwageom stood up, making a croaking sound as if he was being crushed by a suffocating wind.

A dog's net! The Toungung is blaming the net.

What kind of people make and use nets like that!

The correct answer is Lim Ki-Hyeon's Tiger Hunters.

It is said that the tiger can exert a force of eight hundred pounds, and is also fierce and cunning.

On such a topic, since they can't even get hazard pay if their hide is damaged, the usual method is to cover them with a strong net, drive in stakes to secure them, and then beat them to death with a hammer.

Qing is running wild like a female tiger.

The creature called Binho in Zhongyuan is not actually a tiger, but is classified as a leopard in the Qing homeland.

The great Zhongyuan people decided to treat tigers and leopards as the same species, since they were all animals, with the only difference being the pattern on their skin.

The thick and heavy one is a tiger, and the sleek and slender one is a tiger.

However, Qing was like a tiger, so to speak.

There were already two long-legged men hanging from the net.

The Cheonhwageom turns the net over and drags the remaining part on the ground, which is the result of a reasonable attempt to pull it down and knock it over.

But pulling was a no-no, they were dragging each other and fell over, their arms got tangled, and the two shabby adults were dragged along the ground.

And yet, the Heavenly Flower Sword flies around, and when you roll your feet, the Heavenly Flower Sword's new form cuts through the air.

Those hanging from the nets come flying in like pebbles thrown onto the surface of the water.

What kind of strength does this bitch have!

Aduk aduk Toungung's teeth were the only ones that suffered greatly.

However, it is a bit of a Qingdo man's appearance.

With the weight of two men hanging from his back, the net wrapped around his body was pulled taut, causing the flesh on his chest to bulge out as if it were about to burst.

And you're still okay?

Isn't that a woman's weak point?

So it really hurts and brings tears to my eyes.

"Don't you protect your heart? It's a three-headed sword, but you're throwing away two heads? We're not useless lumps of flesh! It's a woman's most vital organ, so protect it quickly!" The protests were surging through me in agony.

The trembling of the corners of Qing's eyes was proof of that.

This won't work. My head hurts so much I can't think straight.

So, uh-huh!

The spirit of the Cheonhwa Sword roughly scratching the neck.

Even if you shout roughly or scratch your vocal cords, your voice will still be beautiful.

As Qing exerted his strength to pull the net, the two creatures hanging behind him were launched into wingless flight and attacked Jangpyeongmundo.

A swordsman wearing a strong sword could neither ruthlessly kill his subordinates nor accept them kindly, so he jumped up and praised the swordsman.

One human weight is pinned to the ground, one's head snapped, another's shinbone exposed to the world with an open fracture, screaming "Aaaah!"

Qing grabs the front of the net skirt and lifts it up as if flipping over a dining table.

A human weight and a corpse float on it, and a heavy net spread out in the air wraps around the super-excited Taoist monk from below.

And as the weight with remaining strength soars high into the sky, Qing quickly raises both hands and raises his chin, thinking this is the moment.

Parachute mesh wedding dress.

It will go smoothly, but in the end, it roughly sweeps the tip of the chin, leaving a bitter pain, but now, three long-sighted people, or rather, two people and a corpse, were tangled together and begin to fall behind the blue.

The blue fish that has thrown off the net feels relieved.

With the weight that had been weighing down my entire body removed, and the pain that had physically squeezed my chest and threatened to burst, I felt even lighter, as if I could fly.

So, just like that, I'm wearing a sandbag.

And then straight away, what was that talkative thing, what was his name? Toin? Was it Toin-gong? How can a person's name be Toin-gong?

Anyway, to that guy who was talking nonsense.

Strong and weak forces collide.

Broken starlight scattering in all directions.

"capital punishment!"

The voice of Priest Yeom Bing suddenly cuts through.

The early stages of the super-climax, yet still unstable and dangerous, were digging in together.

But the Cheonhwageom disappears before my eyes.

The blade of the salt ice cut through the air in vain, and at that moment, Toungung's gaze turned straight down.

Cheonhwageom's posture is like lying down with his knees bent, his feet and back touching the ground. The moment their eyes meet, Cheonhwageom's lying arm sweeps the floor, and the raised giant sword lets out a sharp scream.

The priest's ankle on that track.

"Ah!"

Fortunately, the priest was wearing a protective gear, so instead of being cut off, his feet floated up and rolled around.

"this guy!"

Toungung urgently lowers the sword.

How desperate must you be to not be able to tell the difference between a man and a woman.

Martial arts is a way of dealing with humans, and humans usually don't lie down when fighting.

In other words, the foundation of martial arts was not designed to deal with an opponent lying on the ground.

Bang!

A large sword is driven into the ground, and the dirt bursts out roughly.

Beyond that, the giant buttocks of the Cheonhwageom, which rolls backwards, the back plate, the white, slender neck, and then suddenly stands up-

Rotten flesh in sparkling eyes, camellias withering everywhere, corroded iron, hills filled with corpses and melted flesh flowing down them, all sorts of ominous colors that cannot be expressed.

"K-Killing Sta-"

Deeng!

The majestic sound of the temple bell erases the words of Toungung Palace.

A massive bang brushed past his cheek, a thud, the sound of a person being torn apart into pieces of flesh.

However, Toungung cannot turn his head to see who died, whether it was a priest or a disciple.

The splendid starlight suddenly appeared before my eyes and filled my entire field of vision.

"ah."

The Moonlight Sword pierces Toungung's eyes.

The most vicious murderous intent and resentment that a person can create, along with empty words that no one will listen to, tear apart the brain.

If there is an afterlife, the path Toungung takes will not be boring at all.

Because the disciples and priests would arrive quickly, it would only take a moment for everyone to be reunited.

What kind of girl is that?

By the way, have you seen those plump breasts? Wow, if I knew it would be that hot, I would have gone to a brothel and tied them up.

Huh. Didn't you see that girl using the iron plate bridge right in front of you? If that was a bed, wow, she'd fall over.

They were just chatting away at such pointless things and getting along well, but Sapa's behavior was so-so that they might have headed towards hell.

Of course, there is no way that Qing would know about the afterlife.

Let alone the afterlife, I didn't know about that world when I lived in my hometown, and I didn't know about Zhongyuan even when I lived there.

Of course, I am more ignorant than others.

But the world we know is limited to our own perspective. Since we understand only what we see, that's ultimately all there is to the world.

By the same token, the Cheonhwa Sword is now reflected in the eyes of onlookers, enemies, and soldiers.

In their world, a giant named Cheonhwageom will now stand tall.

A woman standing alone among the gazes that surround her.

The blood-soaked uniform clung to the body, revealing its dramatic curves.

A cruel yet alluring color.

In the silence, the sound of someone swallowing saliva could be clearly heard. Haa, a sigh with a hint of heat.

And only then does a clear voice follow.

"Next person."