\chapter{Chaotic Mess (4)}

The question of which is stronger, a large army or a small number of elite warriors, is an eternal topic of debate among the people of Zhongyuan.

As the saying goes, three fights one.

It is not because the people of Zhongyuan particularly like the number three and divide the heaven, earth, and man into upper, middle, lower, early, middle, and later stages that there were three peaks in one flower landscape, and three peaks in the later stages of one peak, and three peaks in the early stages of one peak.

Because four beats one.

The four-way passing technique that hits from all sides at once is the basic and most powerful means of passing.

So, it's too much for two people to deal with.

If four people face each other, it's an easy win.

A number that is considered to be able to counter three people, an ambiguous number that would allow them to lose at least one defense even if they rushed in at the same time. Three.

So the debate starts here.

So, if we lower the level of the three and instead increase the number, is it advantageous or disadvantageous?

If things got really heated, it would be a heated argument that would escalate into a fistfight.

Statement from the attacker's side.

"Of course, four is better than three, five is better than four, and six is ​​better than five. Even if your skill level is somewhat low, being surrounded on all sides is already a fatal blow. In fact, the rear and back were the most vulnerable points for a warrior. How can a warrior who already has one hand short of dealing with the front, left, and right defend the back? And wouldn't a warrior who strikes an unprotected vital point be fatal, even if his skill level is low?"

Statement from the attacker's disadvantaged side.

"A ignorant idiot is talking nonsense, blocking all sides? No, the moment someone of low skill interferes, it's not like all sides were blocked, but rather one direction is opened. Even if three peaks enter instead of one super peak, the passing will come from all sides anyway, so if four people were the limit, then wouldn't one person be idle? Furthermore, three super peaks don't control three directions, but only two, and the space filled by the peaks is a flimsy wall that can be pierced with a single stroke of a master's sword. In fact, it's a weaker encirclement than three super peaks."

These were commentators who were not hired by anyone and do not receive any compensation, but speak purely for their own enjoyment or to gain authority as a comedian.

Even though it was a commentary, no one acknowledged it or gave it a place like that, so by Qing standards, it could be said to be a primitive ancient personal broadcast.

Commentary: The two's eyes were burning.

"Ha. Anyway, two at the peak of their power would be enough to block with one arm each. So, three at the peak of their power would be far more advantageous. Isn't that simple math that even a three-year-old child would understand? What kind of idiot doesn't understand this obvious principle?"

"Wouldn't it be a real help if we took one of the tiger-hunting dogs and replaced it with a puppy? is there anyone among you who would be more afraid of three wagging dogs than of a wolf the size of a calf?"

"Gentlemen! There’s a moron here who says three puppies were enough to catch one hunting dog!"

Even so, the difference between a climax and a climax is not like that between a hunting dog and a puppy.

People's narrow eyes were turned towards the small group of elite commentators.

If I had heard that, I would have clicked my tongue.

It is better not to make a leap in logic than to not make one.

Originally, when two people were arguing, they can win by just mixing in personal attacks and arguing fiercely, but when they were talking down to the listener, they have to convince the public, not the opponent.

Anyway.

So is it actually disadvantageous or advantageous?

Well, from Qing's point of view.

I rather like it.

Qing rushes towards the Jangpyeongmun warriors.

Qing's left hand is elegantly spread out, showing off his long arms.

"Tathagata God!" "Damage!"

It seemed like they had prepared for it, as the Jangpyeong disciples immediately shouted evasion and jumped away from the diagonal line drawn by Qing's left hand.

Ding. A sound like a bell being struck with a spoon.

Qing-i smiled brightly.

The exceptionally sharp fangs shine brightly.

Water lily.

Hang flowers on a tree to deceive the enemy.

The gains and losses between someone who takes a single step and swings his sword, and someone who is startled and dodges loudly by stepping on the sword, were self-evident.

I move less than others.

Other people move more than me.

So, wouldn't one of the ways to practice this in the world of learning be through the trick of deception?

How great an advantage it would be to create a breach in the enemy's lines with a single blow and find an opening to infiltrate.

Qing steps on the long-legged sword rolling on the floor and steps on the true ground.

The sensation of bones being crushed and crushed, the creaking, the sweet scream of blood boiling inside.

He diagonally blocked the blades flying from left and right with his forearms, and took one, two, three steps in.

At the end of that straight line, there was one Jangpyeongmundo who opened his eyes and froze.

You might wonder how one can be so rigid when faced with a life-or-death situation, but in reality, people's minds turn white and become rigid when faced with unexpected danger.

The first instinct that humans must overcome is a fatal human habit.

So what's this, some second-rate guy? Why did you bring out kids who can't even be hit by unmanned vehicles?

The tip of the blue sword extends gently.

The blade of a giant sword passes by as if grazing the neck.

A large blood vessel next to the cervical vertebrae snaps, and blood spurts out roughly, then thump, thump, in time with the heartbeat.

A strange golden thread of blue that stretches out in an instant.

The smooth movements of the Muyeongshinsu, the best pickpocketing technique in Zhongyuan

Qing accepts the net very naturally, as if it were his own.

Oh. Net.

I've always wanted to try it.

Qing throws the net that came into his hand.

However, there is a secret to a net; it does not spread out and envelop the enemy just by holding it in your hand and throwing it.

A clump of nets flew away and hit the thrush of a long-legged monk!

"100 million!"

Not only was there the weight of the net itself, but the immense force it carried made the long-legged man fall down with his legs raised high.

Thanks to that, the two guys who were following him were crushed underneath while taking out their comrades.

Qing runs away, turning her back on the three men who were trying to make her laugh.

Of course, the Jangpyeong disciples also had a strategy.

If the advanced warriors in front stopped the Qing and stopped them, the rest would block their retreat and surround them, engaging in a wheeled battle.

But as soon as they started, the ranks were breached and the Qing army broke in, so they reached the rear in an instant and exposed the three great disciples.

The world's most beautiful woman takes a step forward, and dozens of sword lights flash.

The 108 Swords of Asura, the seventh second.

Ten thousand and one thousand attacks.

There were ten thousand kinds of beasts in heaven and earth.

A single sword resembles the fangs of ten thousand.

A vicious beast with vertically slit pupils and a yellowish glow takes a huge bite out of the rear ranks of the Jangpyeongmundo.

The blade flashes and blood spurts out, dripping down in drops.

Bloodshed under the sky, chaos on the earth.

The whole place is filled with a pungent fishy smell, um, gulp.

Miss, why is my appetite so upset?

They say he's one of the ten greatest magicians in the world, but he tries to dig in whenever he gets a chance.

The blue calms the rising murderous intent.

"You bitch! You coward!"

"Huh? Me?"

"Is it the law of the party to slaughter the weaker? Can't you come out and fight proudly?"

"Oh?"

The Qing is so absurd.

What were they talking about? They're coming in droves right now-

In an instant, the new blue form splits into eight and rushes in all directions.

A beat later, a net covers the spot.

Eight remnants of the blue cross the sky, each in a different pose.

And one of the dogs, the new one that was moving away one by one with an elegant step, slowly finds the color it was looking for and starts coloring it.

And the net that falls as if to congratulate him.

At that moment, the weight of the net that was entangled heavily made Qing let out a disgusted sound.

What? How?

"Kill him! I finally caught him! Did you think I wouldn't notice after seeing that much?"

The Neungpa Mibo is a formation and tactic that appears behind the target with the enemy's back to it.

Even if it splits into eight, only a few of them run straight towards the enemy's back.

If you prepare and practice in advance, you can cast your net on the spot.

Qing pulls the net left and right.

A high-strength net made of thickly twisted hemp and steel wire is not something that can be easily broken even by the strongest force in the world.

There was a thumping sound, but the connecting parts that tied the horizontal and vertical lines were torn and stretched, but the net itself could not be cut, so it floundered.

The Jangpyeongmun masters, each with their own bet-filled blades raised high, stride closer.

The first to arrive was Toungung, and as a representative, he was a large and strong man who struck down the Qing as if he were going to split it in two.

"Dead!"

Qing raises her hand holding the net.

The net that wraps around the body can also be seen as a weapon in Qing's hand.

The net, with its strong energy, is pulled taut to catch the pottery of the Toungung Palace.

My ankle got caught in the net, so one of my knees went up.

It was a full-force slam, even with my own weight on it, but it was just the net rippling, and the clash of the strong energies just sent sparks flying.

The net, which cannot be broken even by the strength of the Qing, is imbued with energy, and has the strength to block the sword's powerful strokes.

The river crossings that followed flew in.

Qing turns around and holds the taut net between her arms.

Then, the ankles were stretched forward, the elbows were pulled tighter, and the net rope is pulled tighter, forming a vertical line blocking the river crossing's trajectory.

A long-form master is thrown out by an auditory hallucination that sounds like a sound effect that is somehow like a ding.

And as he passes by, another river crossing is about to cut the river.

As Qing lifted her huge buttocks back, her feet on the net rope, and her head was raised high, the taut net rope rippled noisily, bouncing off the sword again.

The parts of the body caught in the net were pulled in different directions to create tension, so the obstacles placed to stop movement actually become a fortress to protect the body.

Hey, this? Defense? Isn't it pretty good?

Qing-i slowly and vigorously pulls her arms out through the mesh.

It was an attempt to wear the net like armor, but the force that suddenly pressed down on my head caused it to fall to the side.

Oh, I guess it wasn't this hole.

Both arms were free to fall, but the head was lying flat because it was tied too tightly.

Thanks to the flexible joints of the oil tank, you can lie completely on your side without nodding off, but for now, the distance, the world, is lying on your side.

Standing on one leg, one leg dangling with the knee caught in the net.

"Don't cut, stab! Where the hell did you get such a tough net? There's a limit, you idiot!"

Toungung shouts.

This is what the person who ordered them to bring the toughest ones just in case said.

"Wait! Wait!"

As he tries to pull out his arm that Qing has caught, he gets tangled in the net instead, and he kicks his feet like a rascal, then slaps the blade that touches him.

Where were you going with the sword in your hand?

With a "bang!" sound, the broken blade brushed past the owner’s cheek and disappeared.

Before the goosebumps from the broken sword could subside, Qing's left hand stretched out, touching the opponent and pouring out an invisible energy!

Deeng!!

With the proper sound of the temple bell, the image of a material refracting in a circular manner based on Qing's hand, a rippling wave.

Jangpyeongmun collapses, spitting out the melted intestines with his mouth.

The sound of the temple bell from the Tathagata Goddess, who has put forth all his might, is louder and more magnificent than you might think.

While the disciples flinched, the net monster, who had even let go of his sword, began to show his palms in all directions.

Ding ding ding ding ding ding!

The Tathagata Goddess of the Blues can imitate a single note. If you were in the Blue East, you'd be shouting, "Wow, school bell!" with her spoon-playing.

The Jangpyeong disciples, who had been covering their own vital points with their palms facing each other, looked at Qing in disbelief.

What was that just now? It was ringing in my ears-

Deeng!

A golden handprint appears in the air, and its giant palm gently touches a single person.

Unlike the smooth movement of the hand, it is a long-range sword that flies one sheet as if hit by a carriage, bounces on the ground, and then flies another sheet.

The fifth word of the Tathagata.

Five elements, Taesuin.

The end of the world that once blocked the path of the Great Jecheon, however, was simply the Buddha's slight opening of his palm, so the finger in front of the ant must have been like this.

"Don’t give them space! It’s more dangerous to give them space!"

Toungung gives instructions again.

The Jangpyeong students flinched as Qing led the way with a loud and noisy chant.

In the meantime, Qing was hurriedly searching for my hair, then grabbed the mesh and put it over my head.

He put his head and both arms through the net and let the long ends hang on the ground.

It is as if she is wearing a Western wedding dress woven with strings.

