\chapter{Chaotic Mess (7)}

The little girl's ears perked up.

The expression is extremely serious.

Anyone can tell that he is using the JiQing technique.

Eavesdropping is the art of gathering and listening to sounds. It is a technique used to eavesdrop on distant sounds or small sounds, almost like eavesdropping.

The eyes of Dang Jin-cheol, the head of the Tang family, who sees this scene, were filled with anxiety.

Of course, it's not particularly new or surprising since it's the same little sister I always see.

But no matter what, I can't just leave the act of eavesdropping on the leader of Wulin alone.

It wasn't just the innocent but curious, mischievous, pretty youngest child who always eavesdropped on the family's affairs, the elders' affairs, the house of the house during a meeting, the mothers' annex, the reception room while guests were being received, or the guest rooms where guests were staying.

So this time, it was time to give him a harsh lesson as a brother, even though it was heartbreaking.

"Ah, no matter what-"

"Shh. Be quiet, oppa."

"That, that won’t work……"

Dang Jin-cheol's stinging reprimand, the end.

Do you know the hierarchy of power in the Tang family?

The Tangnan children were on the top, the medical store, the Mandok store, the ironware store, the gunpowder store, the accounting department, and the Taesang elders who drink tonics like water and were still in good spirits were on the top.

Thanks to that, if you list the mothers of the Dang family, who were far behind in the rankings, and the Dang family head, Dang Jin-cheol, who is the head of the So family, is the weakest one that cannot be included even if you use all your fingers and toes.

So how could anyone dare to defy the true supremacy of the Tang family?

The soundproofing of the Wulin Alliance meeting room is not bad.

It's not bad at all.

The meeting room is not a place to have serious conversations, but rather a place to just chat, drink tea, and ask how they were doing.

And above all.

What kind of scoundrel would dare to eavesdrop on the conversation of the leader of the martial arts alliance?

No matter how ignorant, rude, and ill-mannered a person may be, if they had even a little bit of common sense, they wouldn't have thought of eavesdropping on the conversation of the leader of the martial arts alliance.

There were repercussions for the family or affiliation.

Above all, the leader Jo Hyeon-ryang is a peerless master who ranks second among the ten greatest masters in the world, so how can he handle the aftermath?

But it is possible for a child.

What if I get caught?

Mancheonhwaru, the highest ranking official in the Tang Dynasty!

I was so curious that I did it with tears streaming down my big eyes. Sigh, sob, sob, sob. If I say, "I’m sorry," and bow deeply in apology, wouldn’t I be forgiven?

As it always has been!

So, the child is not at fault.

He was so surprised that he shouted, "Heavenly Blossom Sword!" as if he were the leader of Wulin, so it was only natural that Tang Lan-ah would listen to him.

And then he kept talking carelessly, so even a master like Hyeon-gyeong made a bet and didn't even take the minimum precaution of blocking out the noise.

Why? Because I let my guard down.

Because they didn't realize that the unofficial Sachon Princess and the world's most evil woman in the next room could be eavesdropping.

Of course, Jo Hyeon-ryang is wronged.

Tang Lan-ah, the last martial arts competition was her first time in Wulin, so how could she have imagined that a perfectly normal person like Huggi Ji-su would dare to eavesdrop on an adult's conversation?

And, regardless of East or West, past or present, picking up other people's words and using them to do things is the fate of a wicked woman!

So, the little boy had no choice but to clench his fist and stand up.

"Oh dear, where were you going now? I need to see the leader."

Dang Jin-cheol then calmly stops his younger brother.

Tang Lan-ah looked at her brother like that-

"Oh, right."

"Yes, I understand you’re excited to be leaving Sacheon, but first, I need to meet the leader—"

"Give it to me."

The little girl proudly extends her hand.

"Huh? What?"

"Give me all the gold and poison."

"Oh my? Geumja, let's do that, but why the poison? This guy isn't carrying Grandpa's poison, is he? It's deadly poison—"

"Hurry up. I have a use for it."

"I'm not your family. This isn't your family home, so if you act carelessly—"

At that, Tang Lan-ah's expression changes completely.

My eyes were wide open and twinkling, and a different kind of starlight shines inside my eyes.

With his nostrils still open, he managed to make a snoring sound and smile faintly.

"Oh, dear. Brother. Give me Lan-ah, quickly. Lan-ah needs poison."

"Huh? Um, that won’t work……"

"Brother. Huh? Huh? Huh?"

If Qing had seen it, she would have bitten her tongue and died rather than trying to win him over by acting so cute and calling him by his name in the third person.

Because Tang Lan-ah was a heartless villainess, she does not care about the means and methods.

And above all, because I have known all my life that it works.

"Oh, it’s dangerous, so you have to use it carefully."

Amazing facts you can learn here!

It's less dangerous if you use poison gently!

Tang Jin-cheol keeps taking out hidden weapons and poison bottles from somewhere without stopping.

The girl who received it also tightly packed it into her arms, waist, and chest, and it suddenly disappeared without a trace or any protruding parts.

It is a strange storage technique that not only Tang Lan-ah but also every member of Tang Clan could skillfully use as a basic skill.

"As expected, Big Brother is the best! Then, shall I go play for a bit?"

And then he suddenly got up and ran outside.

Oh, that guy too. He only calls me when he's happy.

I guess you made a lot of friends at the last martial arts competition.

Dang Jin-cheol was practically disarmed after being given all the poisons and secret weapons for self-defense, and he was smiling happily.

The Wulin Alliance actively encourages social gatherings of like-minded individuals.

The more the members of the Jeongpa martial arts world become entangled with each other in positive relationships, the stronger their bond becomes and the greater the power of the alliance becomes.

So, the Wulin Alliance does not spare any support, not to mention encouraging them to get along.

If you write down what kind of activities we will do in what kind of circle and with whom, and submit it, whether it is a resolution or a joint statement, you will receive many benefits.

They invite relevant nouns, post rooms to recruit interested colleagues, and even provide necessary space or facilities for your use.

The Half Sword Ssangdohoe is not a social group that has officially submitted documents to the Wulin Alliance.

But how could Wulin ignore the sight of the Heavenly Blossom Sword and the formidable later ranks of the five great families playing and falling together?

The reception desk at the social gathering is worried that people were late and not coming to register, and that this will turn into a senior citizens' gathering.

It is a high-ranking sect where all the descendants of the Five Great Kings were included in the Heavenly Blossom Sword.

Even that activity wouldn't be a healthy non-profit (plus a restaurant tour).

Wouldn't it be great if it became widely known and became an opportunity for the reviewers to share their insights and develop together?

In fact, most of these top-tier social clubs do not bother to register with the group and just enjoy themselves among themselves, so it is just a pity that the reception department is not doing well.

However, there was not a single member who wanted to apply for the extraordinary name of the Half Sword and Double Sword Club, saying that Half Sword is a sword and Double Sword is a sword.

There will probably be no future submissions.

Anyway, since it is a double sword society like this, the Wulin Alliance also quietly gives them some convenience.

For example, even if you enter Mucheon-gak, the highest-class guest house of the Wulin Alliance, without permission, the maids will tell you to treat them well.

Even though they use the backyard as their own private training ground, they manage it without saying anything.

It is a silent permission that has been given subtly.

As things went on, the members of the Half Sword Sword Association naturally settled in MuQinggak after joining the Wulin Alliance.

The members who were still sitting down and chatting today were Ok Gi-rin, who took refuge from the women and settled down, and Maeng Shin-hyeon-noe, who has already brought a lot of iron bars and weights for strength training.

Peng Daesan was swinging his sharp sword, and in the corner, Zhuge Lixian was sweating profusely while striking the weight.

"Huh, you're all playing around? Qing'er is gritting her teeth and fighting against Unorthodox's group right now, so is this the time to play around?"

The girl who suddenly appeared scolded him.

It's absurd that a girl I've never seen before suddenly appears and raises her voice.

But more than that, I care about the content of the words.

"What does that mean?"

"What do you mean? Literally. I'm going to help Qing. You can come or not."

Tang Lan-ah started telling the story in a very lively manner.

What about the killer-among-killer, what about the Thousand Flower Sword, what about the apology?

No, Sister, killing!? were you talking about the blood-absorbing magician of the Shin family from 180 years ago? No, Yun Yuanying!? No, Sister, no, the former patrolman, no, the apology!? You know the apology! This comes from the anecdote of Insangnyeo and Yeompa of the past state of Zhao, and is also called BuhyeongQingjae, the noble sound? were you listening? Sister Tang? and so on.

But since Tang Lan-ah came to inform them rather than have a conversation, she didn't respond.

A villainess is not a good listener.

"No, Qing'er too. If something like that happens, why only told Young Sword King in advance to go together-"

"Wait a minute, Brother Nan-gong went with her?"

Somehow, Paengdaesan's eyebrows twitched.

But Tang Lan-ah didn't notice.

Because she had no interest in Peng Daesan.

"Huh. Why is that Sword Flower going anyway? So are you going to go or not?"

"Hmm."

Peng Daesan releases a unique, heart-melting, ultra-low-frequency moan as he sharply sheathed his saber.

It means to go.

There was a time when Tang Lan-Ah thoght that was so cool, but now he was just an eyesore. 'Did he get thought that was a cool looks?'

"Shouldn't we go right away? But can we do it alone? We need to notify the Aliance's combat unit and bring at least one instructor—"

"Didn't you hear what I said? I told you that Qin'er asked them to refrain sending support. If you bring an instructor, what will become of Qing'er?"

"Uh, um. Yes."

So, does that mean that the three direct descendants of the Five Great Families didn't count as the support of the Wulin Alliance?

However, since Zhuge Lixian had the body of a beast but the mind of a wise man, he realized that it was wise to keep his mouth shut and join in for now.

So, the Half-Sword Double Saber Society (partially) sets out.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Next person."

Qing stands alone, wearing a bloody robe.

Although she didn't make a sound, her chest was rising and falling, and she was gasping for breath.

Since it was an area that naturally attracted attention, everyone was able to quickly recognized Qing's condition.

The avengers' eyes light up.

'She's tired, so isn't now the time?'

'Isn't she a little hurt? She's covered in blood, so I can't tell if it's her own or someone else's.'

It could be said that it is really pathetic to try out various methods, whether long or short, while seeking revenge.

Revenge is only revenge if it succeeds. If it fails, isn't it just dog death?

So, the avengers were gritting their teeth, wondering whether they should come forward now or not. They were watching to see who will fight here and relieve some of their strength and inflict some wounds.

But in the end, no one comes forward.

Because this time, I realized something new: even if you fill in a different number instead of the super high-level one, you will still receive a life or death decision.

Since the apology process is not even halfway done yet, there should be plenty of time to prepare thoroughly.

It would be really great if the experts in flower arrangements would step forward in times like these.

Even the best flower arranging experts find it difficult.

For a young martial artist like Hwagyeong, going up against a martial artist of such high caliber is in itself a humiliating act.

If only I could win easily.

Not only is it a defeat, but the moment you show even a hint of a close match, you will be completely embarrassed by the world.

But is it possible to win unconditionally?

Having witnessed the life and death struggles, she is a truly ghostly woman when it comes to the original purpose of martial arts, which is to kill enemies.

A subordinate just below him who is good at irregularities and improvisation.

He is the opponent that experts hate fighting the most.

Whether it's a weak sword or a strong sword, it's all the same, so if you get stabbed wrong, you'll get injured, and injury will soon lead to defeat.

So, the experts of the flower world were still diligently observing and trying to reduce the variables as much as possible.

Besides, since they attacked in a group this time, there will be more of those types of people in the future.

Then there's no need to rush, right?

So no one comes forward.

But to the masses who do not know how to understand such circumstances, it has a different meaning.

If one person shuts the mouths of many enemies, isn't that the mark of a truly peerless master of all people?

So, the spectators' mouth were itching again, they couldn't wait to tell the story of this amazing miracle.

'Hey, listen up. I've been to a place where Heavenly Blossom Sword performs a life-or-death battle to resolve grudges, and well...'