\chapter{Chaotic Mess (3)}

The attitude of a warrior facing a life-or-death situation can be expressed in one word: taking care of one's personal affairs.

Before a duel that might be my last, I'm going to poke fun at my acquaintances, reveal some of my innermost feelings that I don't usually share, and write down what I'll say in case something goes wrong.

Or, you just waste the remaining time meditating and holding on to weights.

But Qing played well.

Eat well, drink well, and chat about studying abroad with the scholars of Wang Xizhiji House.

So, even Wang Ssangryong dared to think, is this right?

It was an impudent thought that occurred to him the next day when Qing, who had been having fun and resting well, ordered that the rebels set up a fighting arena.

Of course, the great ability of a high-ranking official is to twist even his own thoughts.

I wonder if it wouldn't be the true loyalty of a subject to have a different mind from the beginning, as it might suddenly burst out in the midst of a panic while thinking of something impious.

So, I roll the dice of unholy delusion again, wondering if perhaps Madam has no thoughts.

Twin dragons!

As expected, Madam is amazing!

He must have been enjoying everything so leisurely, never even thinking about losing!

Madam is strong!

Anyway, Qing was slowly removing the threads in the dedicated barracks.

The removal of stitches from a stitched wound is usually done at different times depending on the thickness of the skin and the degree of tension.

As a female doctor, Qing is capable of handling the work of one person, so she knows a lot about these kinds of questionable tasks.

Face for five days, head, stomach, and chest for ten days, back, legs, etc. for five days.

However, Qing knows that her resilience is also on a different level than the criminal.

It was roughly three times faster.

A miraculous body that reduces the number of injuries sustained in the six weeks of Qing's hometown.

In Zhongyuan, there is no custom of grouping seven days into a week, so this is the expression used in the Qing hometown.

I tried to cut the knot with my fingernail and pull it out, but it was a little scarred.

The vague scar will slowly subside and disappear over time anyway.

However, I heard that there is a stinging medicine called Jechangsan that melts away the scars and erases them, and that it does not poison the wounds.

What the hell kind of body is this?

Well, then, hmm. Good idea.

It's just too sturdy.

Because if you were a martial artist who deals with the mysteries of the universe, your recovery will be quick.

Compared to the same level, it's not that fast, right?

Originally, the recovery power of unmanned units was on a different level from that of civilians, so by the time it reached its peak, it would have been about twice the base level.

I'm just a little bit faster there, but I don't get infected.

AC. It's all because of your constitution. Constitution.

But that constitution, um, I don't know...

Qing, who has stepped on a landmine for the first time in a while, enters the arena with an uneasy expression.

Qing has a sullen expression, but to others, he looks solemn and dignified.

Now, chairs were placed under an awning on one side of the arena.

Since there was no one to come out, I had to install it in a hurry twice, and it seems like they created a waiting area from the beginning.

When you're feeling down like this, if you just move your body a little, you'll feel better.

As I pass by, it seems like there were quite a few people practicing their skills while getting ready for the exam, but I wonder if there will be anyone rushing in today as well.

It'll be a bit difficult if we fight later.

That's how Qing sips her cold tea.

The sour and sweet fruit tea swirled around my tongue, making me feel a little better.

Qing looks down at the frosted teacup.

A beautiful face blurred across the ice-covered cold car with the help of the Bingbaek Shinkong.

Sweets were expensive.

If the Westerners of this period knew, they would go crazy and say that the sweets from Zhongyuan were so cheap that even children from poor families could sometimes eat them.

Still, isn't Zhongyuan the greatest empire of the present age, and a country where even the lowest class peasants fry meat in cooking oil?

The reason why civil servants somehow manage to get by while the local thieves and gangsters with knives reign supreme is because of this abundant natural resources.

Of course, Qing doesn't know the details anyway.

Even if I knew, I would have just let it go and said, "You should have started a revolution." (That's why I started a revolution.)

It feels like yesterday when I fought a bloody battle with beggars over a rat (and got beaten up unilaterally). Sometimes, I even dream about it.

Now I'm drinking fruit tea with lots of honey and wearing nice clothes.

So this is what they mean by living a life of luxury.

It was a precious fruit juice that was too good to eat alone.

Master, Teacher, Heemae, Grandfather, members of our Half Sword Ssangdohoe, Xue Ga-nom and others, etc.

It would be nice to have someone by my side.

Honestly, yeah. Life is good these days.

It's worth living, it's really fun to live.

Because every day is fun and exciting.

So, I guess I should stay here.

A bitter smile spreads across Qing's face.

So we have to fight.

It's not like he's a bad guy or that he cuts people and his nerves tingle with electricity.

First, go to Hwagyeong and then go to Hyeon-gyeong.

I have to see the end of that great woman, the destroyer of the world, and I have to settle things with Taechang.

"I need strength-"

I'm not buying it. Go away. What kind of peddler were you?

The previously calm evil voice whispers again, and Qing shoos it away like a fly.

Then suddenly?

In the central plains, there is something called a chachim.

A sharp stick used to prick and clear out clogged tea leaves in a teapot.

And then, place the teapot in the middle of the teacup and swirl the cold energy of the salty ice-cold water.

Ice cream cone complete!

Because the teacup was so swollen, the shape of the ice cream was also swollen, and ended up looking like a lump of bread.

Qing's tongue flicked out.

Crushing with a bite stronger than that of an animal.

Slurp down the melted, flowing fruit tea.

Crunch crunch crunch slurp.

It was a truly breathtaking sight.

Isn't she the most beautiful woman in the world, licking her tongue and eating ice?

So what do the onlookers think?

I rather like it.

People came to watch a life-or-death revenge drama and a breathtaking bloodbath, but they were so fixated on it that they think it was worth it just to see it.

However, the Avengers were seething inside.

Some people were just waiting for their turn, keeping an eye on the situation before taking revenge.

That sworn enemy was very lively.

It's not like I'm making fun of anyone, what kind of obscene and vulgar thing is that!

Actually, it's a joke.

I know that it's not a good idea to show up in front of so many people.

But look at the appearance of those avengers.

They're just waiting for someone to step up and hurt them and take their energy out, so they'll get fired up and attack.

It was a kind of wide-ranging provocation.

If you're going to get upset, don't worry and come out quickly.

Did it have any effect?

"Oh."

"Oh my, I think they’re going to fight."

Finally! You're here!

Qing stands up from her seat with her eyes shining.

But were you alone?

Hwa-gyeong? Hmm. Hwa-gyeong is a bit tough.

For Qing, one Hwagyeong is more difficult to deal with than three Super Climaxes.

It is common knowledge in the martial arts world that the initial stage of the Hwagyeong is similar to the combined attack of three people who were at their peak of synergy.

However, for Qing, who uses his immense internal energy and a small amount of defensive power below his elbow, Hwagyeong is a more fearsome presence.

After all, Hwagyeong's energy is so intense and its density is different, so even if it's a self-defense energy, it'll just end up being torn apart.

Qing quietly draws his sword as tension slowly rises.

Finally, the man opens his mouth.

"I am Bunggeomcheonri Toungung, and I wish to indict you for the crime of murdering the head of the Fujian Jangpyeongmun clan. Do you admit to this crime?"

"It seems like among those I've cut down was a Somunju? If they had at least announced their names, they wouldn't have committed the outrageous act of severing the lineage of a sect. What a shame."

Toungung ground his teeth at that.

Since I didn't reveal my name, I don't know if I did it or not, and since I didn't reveal my name, it means I made a surprise attack without even revealing my name, so it must be my fault. It was a sly remark.

Then Qing said, "Oh no."

Yeah. Be fair and square. Don't provoke me unnecessarily.

Still, wouldn't it be better to turn the eyes of a master of Hwagyeong upside down to be a worthy opponent?

But that's funny.

If you spread rumors, should I put the knife away?

That was when Qing thought so.

"Cheonhwageom. You said you'd take on three supreme beings. So, how many supreme beings can you replace with one supreme being?"

Oh, you came to inquire about a duel, not about Hwagyeong.

Qing answers with a smile.

"How many people did you find out about?"

A tendon suddenly appears on the warrior's forehead.

What the heck? It's funny to see people being made fun of. Ha, strangely enough, I'm getting angry.

Qing is being treated unfairly.

Because this time it was a real act of kindness.

I just said I would do whatever you wanted.

"Haven't you reached your peak of power? Don't even think about evading the truth. I've seen you achieve divine union with my own eyes—"

"That's right. A super-climactic review. So, what were you trying to say?"

Usually, people with long tongues like this were scammers.

Qing kindly interrupts him and tells him to speak quickly if he has anything to say.

"……A warrior in the late stage of the peak can deal with two warriors in the mid-stage of the peak, and three in the early stage of the peak. One warrior in the early stage of the peak can deal with three warriors in the late stage of the peak, one warrior in the late stage of the peak can deal with two warriors in the mid-stage of the peak, and three warriors in the early stage of the peak. One warrior in the early stage of the peak can deal with three first-class late-stage warriors, and one first-class late-stage warrior can deal with two warriors in the mid-stage of the peak, and three warriors in the early stage of the peak, and so on and so forth……"

What is this?

Are you measuring the water for noodles on some kind of scale?

Is this a math problem?

I want to adjust the salt content to five centimeters per liter of water.

If we add the same amount of salt as the salt content of the soy sauce, which is 2.5 points, and the same amount of salt as the salt content of the soy sauce, which is 1.5 points, what is the total amount?

Qing blinked her eyes.

The onlookers who were excited, thinking that they were going to fight, were speechless and fell silent.

No, it's not like Ichiya is wrong.

I'm going to roughly match the general combat power and put it in.

Qing sighed deeply and answered.

"Okay, just do it."

"Wait a minute. But here's what we need to consider: while it may be logically true, in reality, the greater the gap in skill, the more difficult it is for the subordinate to demonstrate his or her skills."

"Okay, so come as you have prepared."

Qing cut off Toungung's words.

With this many people, I have no desire to say hello.

As a result, there were six people with two super-climaxes, six with a mix of first-class early-middle-late, and ten with a mix of first-class early-middle-late, and a bunch of second-class bastards.

However, the nets in the hands of each of the Naburangs were a bit, this time, Qingdo is a bit more absurd.

"ha……."

Qing sighed, wiping her forehead.

Even the onlookers thought this was a bit too much, so they all looked at the shameless avengers with frowning faces.

Qing drops her sword.

"No more words were needed. Blood for blood."

People exclaim, "Oh!"

How can the figure of the young girl, standing proudly in front of such a large number of enemies, be so noble and beautiful?

And so, with the shout of "Strike, Toungung!" and "Waaaa," the enemies rush in like waves.

She raises her sword.
