\chapter{Chaotic Mess (9)}

In the end, since there was no one who would act like a man until the day Lim Ki-Hyeon left, those guys who always talk about being great men and such were the most well-behaved, so you have to cut off the peppers.

So, after three nights of sleep, the camp is bustling from the morning.

The destination is Huaiyin County, Jiangsu Province.

I know the geography of Zhongyuan to some extent now, but I still don't know the history of the Zhongyuan.

But from Im Gi-hyeon to Hoe-eum-hyeon is 600 li.

By Qing's side was the world's greatest general (probably) Wang Shuanglong.

In Zhongyuan, a loyal subject is like a tongue in the mouth, saying what you want to say instead of what you want to say, and filtering out only what you want to hear.

This is contrary to common sense, so you might ask, if that is what loyalty is, what will become of the country? Wouldn't the country be ruined?

So it really failed.

Up until now, countless royal families have fallen due to the devotion of such loyal subjects, and this can be said to be the rise and fall of a nation.

And the next city, Hoein, is the hometown of the famous Han Xin, a man who was not loyal.

Hanshin is 'the one who crawls under the ground'.

If Hanshin were a woman, it might not have been a big problem, but Hanshin is a man.

Hanshin was one of the common gangsters of Hoeinhyeon.

However, he was outstanding in military affairs and served as a general under the command of Liu Bang, the founder of Han.

Afterwards, for his achievements, he was granted the title of King of Jiangsu Province and returned home in glory.

However, he was a very, very good person.

How much noise there was in his hometown after he returned home successful.

Considering Han Xin's personality, which was arrogant in itself, he must have been thrilled to be arrogant and arrogant every moment until he was beheaded for treason a few years later.

If you can endure the humiliation of crawling under someone else's legs, you might think of an ambitious man who looks forward to tomorrow.

But Han Xin's disgusting personality is very famous.

This is a character that kills his comrades and endangers the country in order to monopolize the credit.

It was a shallow scheme, thinking that a capable general would be needed only when the country was in danger.

Even to his lord, Liu Bang, he gave a cocky, snickering expression and said, 'To be frank, wasn't it me who created the unification of the country? After all, Your Majesty's military capabilities were only a tenth of mine. And that's a generous amount. Haha!'

He was a man of such character and who spoke such words in front of His Majesty, so of course he deserved to be beheaded.

Rather, the breasts were the heavenly personification.

But I tried to overlook him until the end, thinking that he was a bit rotten, had no conscience, was arrogant, and was greedy, but he wasn't a bad person.

"Hmm. He's a bit more stupid than I thought. Everyone was talking about excessive greed, the greater good, and Bae Soo-jin, but he seemed like a truly amazing person."

"Ahem, his military talent was impressive, but no matter how capable you are, it's the words of someone without virtue. A loyal subject shouldn't expect anything in return from his lord, but should instead consider what more he can do for his lord. Oh, I personally, Madam, have roasted some yu-baegi. Would you like to try it?"

"Wow, Yoo Byung!"

The yu-byeong is about 500 layers of primitive ancient candy.

You can add just fruit, fragrant vegetables like green onions or cilantro, or even minced or large pieces of meat.

"What’s inside?"

"I didn’t know what you’d like, so I grilled them in different varieties. Sweet, mild, fragrant, and meaty—they’re all different kinds."

"Oh. You didn’t do it because of me, did you?"

"Ahem, I just made this because I was bored during a long break. There's no other purpose to it, right? It's just that I tried it for the first time, and I was wondering how it tasted."

"You don’t have to do that. Ah, yum. Okay. Oh."

In fact, in Qing's hometown, where people eat almost anything that humans can eat, they say it is a dog's tongue.

Because they lived by eating things that people cannot eat.

Because her threshold for deliciousness is lower than that of a neighborhood dog, she enjoys eating dog food, saying that it has its own flavor.

Anyway, wow wow. Chopped chopped. It's delicious.

"Wow, General, you can set up a reastaurant."

"Haha, thank you."

Wang Ssangryong bows his head as if embarrassed.

But, is that really a compliment?

Would it be okay for a commander commanding ten thousand troops to set up a restaurant?

Anyway, Wang Ssangryong smiled happily as he watched Qing, who was carrying Yu Byeong without hiding his joy at all.

It's not that Qing eats well.

How could you shamelessly tell your mother that you were eating it, that you were chewing it but not swallowing it, and that you thought your cheeks would burst?

I just accomplished something today.

Whenever the mother sees Yu Byeong from now on, she will think of this general's loyalty.

AKA, a life-like, association-type truth-finding operation!

It was a very scary plan by Wang Ssangryong.

It was a disease that was so meticulously planned that it even went so far as to deliberately burst the side with clumsy skills!

They march and march, carrying snacks like that, riding back and forth on white horses, and the soldiers' morale never goes down. They were truly elite soldiers who were not afraid of the servants of the white horse.

So, perineum!

It is a huge city that grew along a huge canal that runs directly from Gaepoongbu.

Among the natives were Han Xin and Wu Cheng'en, author of Journey to the West, the most popular novel of Zhongyuan.

And the specialty is salt.

It is a transit point for salt that extends inland via canals, and an entire street is made up of salt warehouses to store salt produced in Jiangsu, Zhejiang, and Shandong.

This was a fact that Qing found out by hearing a report directly from the branch manager of Hoeumhyeon.

But why don't you report it to me?

And when talking about perineum, we cannot leave out Hong Taek-ho.

It may not be comparable to Gangnam, which is surrounded by Taeho or Seoho, but any city surrounded by a large lake will inevitably have a developed entertainment scene.

So, what a drink to have while looking at the lake scenery!

On the first day, as always, the general was treated with a beggar next to him - the thoughts of the king and the branch chief might be a bit different - and they ate and enjoyed themselves.

By the way, this is already the third city.

There is no need to stay in Hangzhou for four days, so the only cities left for the duel arena event were Taizhou and Suzhou.

So, as a turning point in the middle, we will probably have to reduce the number of enemies.

So how?

I have to make them jump.

The second day was spent just playing around.

It is a pity for the crowds that followed him to see the life-or-death match.

But since we're always confident that we'll definitely have a duel, we just pass the number back to each other later.

After playing for a day or so, I thought, "Oh, there aren't many days left for this duel."

If he gets seriously injured, the military might block him, so we need to instill a sense of caution that he might retreat without even being able to raise a sword.

In addition, a neatly constructed arena was erected in the garrison and a sign was hung high above it.

"If we were mortal enemies, you wouldn't be able to live under the same sky, but since no one asked me to decide life or death, I realized that my grudge wasn't that deep or serious."

(You said you were my enemy, but you didn't even attack me. were you really my enemy?)

"They risked their lives for Demonic Art in the first place, and jumped into it with the resolve to die, so it would be a great insult to them to accuse them of being wronged."

(Don't you feel bad about seeing those dead guys?)

"Also, even if they had obtained the Demonic Art, it would only have given birth to a great evil, a demon that sucks the souls of the world. So, you must all acknowledge that I have done the right thing."

(Well, I just killed the guys that's deserved to be killed. Do you admit it?)

"So, let's go to the scenic Hoeumhyeon and enjoy the view of the beautiful Hongtaek waves instead of fighting a cruel battle."

(If you're not going to come forwardd, I'll just go play around.)

"This girl set sail and enjoyed the wine with Miju. As it was indeed as famous as Hangju and Soju, I would like to capture this emotion in calligraphy and painting and leave it as a memory today."

(I also enjoyed playing around, so I will play more.)

"If there were still grudges to be resolved, please write your resolution and name on the pillar below and we will consider it."

(If you want to fight, leave your name and sign it with handprint. Then I'll think about whether I should fight or not.)

If it were translated, it would be like this.

It was a beautifully written, pitiful mockery.

The crowd was amazed at the words and said,

'Wow, this feels so refreshing.'

'I told you I've been waiting for you all this time at Lim Ki-Hyeon's office. I'm just keeping an eye on you, taking revenge or something. Ah.'

It seems that the Cheonhwa Sword had more nasty temper than they thought.

But isn't what she said true?

If you were looking for the magic and got lost, wouldn't you really be dead?

Even if they actually found it because of the magic, it would only result in the creation of a great demon head. They were guys whose intentions were extremely evil from the beginning.

So, it is no wonder that angry cries echo through the arena.

"Arggh!" "Euaaaah!" "Heavenly Blossom Sword, that bitch!"

And there were those who just smiled bitterly and walked away.

Isn't this a truly amazing technique?

After leaving their names and handprints behind, they can no longer stalling for their turn.

It's like Heavenly Blossom Sword is declaring to the world that they were enemies who cannot live under the same sky for even a single moment, so if they keep crushing them, they will only be pointed at and it will be difficult to make excuses about waiting for the right time.

What if I don't leave it behind?

Isn't that what you mean by continuing to play?

It's not just that Heavenly Blossom Sword is playing that makes my stomach hurt.

Because I withdrew from a situation where I was trying to resolve it with a life or death decision, I ended up having to endure all the pointing fingers from the world, calling me a coward, a coward, a weakling, etc. until I got my revenge.

If there were only one or two witnesses, I would ignore it, but unfortunately, the five cities were famous for being prosperous.

And between the prosperous cities, roads were built and large cities bloom in between.

If you were talking about breast implants and perineum, there were four cities that were famous for their size that you can stop by and stay in during your period.

So, the number of people who came to see the life and death match increased.

The population of Huaiyin County is the same as that of Nanjing, the capital city, so it is difficult to handle even the people of Huaiyin alone.

So, those who want to give up give up and wait for the future, but only those who feel they must swing their swords once step forward with their eyes shining with anger.

It's an obvious trick, but I have to give in.

The Avengers quickly stamped the paper with the seal and stuck it under the pillar.

So many pieces of paper were stuck together and fluttering in the river breeze, or rather, the lake breeze.

It was a truly passionate cheer.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

the next day.

Qing eats a hearty breakfast and heads out to the arena.

"Oh."

Just look at the atmosphere after saying that one word.

It looks like he's going to chew everything except the gold teeth.

But Qing just smiles mischievously.

I've searched all the flower shops. Today is the day I go to the flower shops. Just wait there.

But what should I say when I go to Hwagyeong?

When this body enters the realm of flower, it is truly beyond the realm of flower, and cannot be expressed in words like ordinary realm of flower.

Well, I have something to believe in.

"Is that okay?"

"Please watch carefully. You know the signal, right?"

Anyway, I can end the duel however I want.

If it's hard, just take it out, that's it.

If you hold on tight and don't let go, then there is a real desperate measure, a last resort that no one has any choice but to give up.

If you say that it can't be helped because it's a woman's body, and that women originally have a few days in the month when they need to rest, that's the end of it.

Well, I'm embarrassed to say it myself.

No matter how much you lose face, this is the ultimate skill of a female warrior that can never be defeated.

However, this does not mean that Qing is cowardly.

In the first place, what kind of fairness is a battle?

Those who rush in after seeing all the foolish tricks to catch an injured and tired opponent, what do you think is so shameless?
