\chapter{Chaotic Mess (10)}

The crowd looked at Qing and blinked.

What is it? What were you carrying? What the heck is that?

In addition to the large longsword slanted on his back, he also held a long, heavy weapon in his hand, the very essence of a military weapon called a Crescent Blade.

It is also called the Guando, and the Green Dragon Crescent Blade, said to have been used by the ancient Guan Yu, is famous as a representative weapon.

Of course, during the time Guan Yu lived, the weapon called the Crescent Blade did not exist.

This weapon appears at least five hundred years or at most a thousand years after Guan Yu's death.

Luo Guanzhong, who wrote Romance of the Three Kingdoms, may have been a history buff, but he was a total idiot when it came to historical weapon research.

Is five hundred years a normal amount of time?

The writing that Guan Yu wielded the Crescent Blade is a serious distortion of history, like the claim, in Qing's homeland terms, that a certain naval admiral during the Imjin War shouted, 'I still have three nuclear submarines left!'\footnote{Admiral Yi Sun Sin. He was dismissed after winning several campaign againts Toyotomi Hideyoshi's expedition. But then the Korean navy suffered catastrophic loss after his dismissal, so he was quickly reinstated back. When King Seonji sent an edict ordering him to abandon the warships and regroup under the ground force, he wrote back 'your servant still has 12 ships left'. He then proceeded to win an overwhelming victory in the Battle of Myeongnyang, 12 ships plus his flagship against 333 Japanese ships. Actually, the Imjin War is currently happened in this novel timeframe}

However, whether it's the Panokseon\footnote{A type of warship used in 16th century Korea} or the nuclear submarine, the result will be the same, and the nuclear submarine story will be much more interesting and persuasive.

So, even if Na Gwan-jung knew, as a novelist and not a historian, he might not have been able to tolerate it.

Guan Yu uses the Azure Dragon Crescent Blade?

82 pounds? Could a normal human swing something like that?

Of course it doesn't make sense, but it's cool.

According to the military books of Zhongyuan, the Unwol-do is the best of all weapons, that is, the best of all weapons.

This is in contrast to the theory of the strongest sword that most martial artists talk about, that the sword is the most perfect weapon.

Why is that?

Well, if a martial artist uses the Unwoldo, the country won't let them off easy.

It is a cutting-edge secret weapon that must be clearly stipulated in national law and must not be used by ordinary citizens.

What if I get caught holding it?

You were a traitor.

Are you the only ones using good things? It's a shame, but the weapon that imitates it is the Nanga Bong, a mass weapon with a hammer attached to the end of a long pole instead of a blade.

And while Qing was organizing the martial arts workshop last night, he discovered that an unknown martial art had been pre-registered.

What is it? A Gyeongcheon Daeseongmagon? A red border?

It's only red, but where did you find this?

When I think about it carefully, I think it was the very same martial art that caused the bandit leader to fly up and fall in the shape of a human meteor.

Imagine the sight of the sky soaring and pouring down like meteors.

As the invisible shockwave spreads out, the ground flips over and rises, and the intense light at the center covers the world in black shadows.

Then a mighty heat burned everything, shattering the shadows and burning them to pieces, and I became death, the destroyer of worlds… … .

Oh, this is awesome.

If it were as Qing imagined, it would be the Great Heavenly Demonic Power. No, it wasn't even a martial art, it was simply the release of a massive amount of heat through nuclear chain fission.

Well, of course it won't have that much power.

But where is the means to fall sharply from the air?

In addition to that.

It is said that when the Qing army was moving and eating and resting, there were elite soldiers who would swing their swords and perform military exercises as if they were showing off.

According to Wang Ssangryong's explanation, it is absolutely not meant to be shown to anyone.

The elite soldiers of Shandong Army originally exercised like this to digest food after eating.

This is truly an admirable business spirit.

As expected, there were elite soldiers under a great general, so when I gave him a janggu, Wang Ssangryong smiled like the happiest person in the world.

Just watching, I somehow feel like I know what the next step will be, yeah, that's how it should be.

Hey, isn't this the Moon Lady Sword?

Yes, that is the Moon Lady Sword.

It was the first martial art to appear in the world, and it made the soldiers of the Yue Kingdom soar, and it has been a military art that has developed into the basic military skill ever since.

If I had to say, it is a deteriorated version that has lost the true form and spirit contained in martial arts and only imitates the outer shell.

This will be roughly equivalent to a trial version of the Moon Sword.

So, should I try using the Blue Dragon Crescent Moon too?

Besides, the distance between the two is ambiguous, so it might be helpful to try out various weapons.

There's also a martial art that deals with soldiers?

So, the Great Seongmagon of Gyeongcheon, the Great Seong!

However, after being forcibly injected with the Kyungcheon Daeseongmagon, I thought that if I hit the ground with the blade, it would break after only a few uses.

Then what? Let's put on some iron hammers!

The result is a sword made entirely of steel, with a heavy iron hammer attached to the other end, and a vicious soldier with a sword in front and a Nanga Peak behind.

Thump! Nanga Peak's iron head hits the ground, raising a cloud of dust.

It was a ignorant lump of iron weighing a full twenty-five geun, so it was too much for even the earth to handle, so it had no choice but to make a fuss and kick up dust.

"Many people have stamped their seals to prove the division, so the unmanned must resolve the grudge in their own way."

At those words, the warriors looked at the blue dragon, or more precisely, the Nanga Woldo standing straight on the ground.

The unmanned in the unmanned way.

However, the moon sword is a weapon prohibited to unmanned personnel.

The statement that it is a weapon forbidden to unmanned personnel and therefore cannot be used by anyone means that it is an unfamiliar weapon that even experienced combat masters have never encountered.

The people there were making a fuss.

"Hmm."

"But I haven’t heard that Heavenly Blossom Sword uses the Moon Sword, so it’s not like he can’t use it skillfully, right?"

"Isn't your intention too transparent? You're trying to conceal your martial arts and seize victory through unfamiliar weapons. No, and yet you're so brazen about it?"

"That’s so shamelessly mean……."

But the crowd doesn't know such deep circumstances.

Come to think of it, I wonder if there has ever been a warrior wielding a sword before.

Or it would be heavy. Can you swing it?

"If anyone wants to hold a grudge against me, let’s untangle the knot right here."

The battle of wits begins again.

Didn't you say you were going to decide today?

No, but I didn't know you'd come out with a moon sword. You want me to go out first and act as a teaching aid to show you what kind of techniques you'd use?

"You're not here? That's strange. So many resolutions were signed yesterday. Well, then, um, Pastor Chun? Could you please read the resolutions? It seems like you're out of the office for some reason, having left the resolutions behind."

Then, on the other side of the arena, a man called Cheon Samok suddenly pulls out a thick slingshot.

Enemies who were a source of contemplation for him.

Are you going to call my name here?

Your name was called, but you didn't come out?

Throw away your grudge? Run away, even putting your name on the line?

Even in front of so many people.

Is there anyone who doesn't recognize the face of the unmanned person who was called?

At that moment, you just have to wear the cowardly label until you kill Heavenly Blossom Sword.

What if Heavenly Blossom Sword is killed by someone else?

Then you have to carry it around with you for the rest of your life.

The enemies found the Qing very ridiculous.

You should have known how well Qing's mind worked when it came to fucking up his enemies.

"Let’s see, Sungwoon Joo from Anpil! is there a guest named Sungwoon Joo from Anpilhyun!?"

"It’s here!"

A man shouts urgently at him.

And then he lifts the dumpling he took a bite of and holds it high.

"I didn’t come out because I was skipping breakfast! Just wait a minute!"

The enemies frown sharply.

That damn bastard, he just got away by himself?

And now, after taking a bite, what kind of meal is this?

"Hey, give me one dumpling too."

"How much is that duck noodle soup? Hurry up!"

Thanks to this, the snack vendors who walked around carrying food on their shoulders were very happy.

It was also a moment when the crowd's illusions and longings for Wulin were gradually being shattered.

Is that unmanned?

Those who were so arrogant and arrogant in front of us, threatening to cut off our breath if we make a move, were they eating snacks to avoid their enemies?

Oh my god, you fucking bastards, you're getting over it now?

I've thrown everything aside during this very busy time to come and see, but these pathetic guys don't even seem to have any intention of fighting over their enemy.

But, wouldn't they be angry if they were enemies?

All we have to do is postpone the situation and watch that arrogant behavior as the year of the enemy approaches.

The enemies were not stingy in expressing their anger. They would chew and chew dumplings, noodles, and pancakes, thinking they were pieces of flesh.

"Well, everyone's eating. Let's see, Pyeongdo, oh Pyeongdo. Gu Jun-on of Shandong Pyeongdo, is that Gu Jun-on, the head of the Heukhomun clan?"

This is Pastor Cheon, who is from Pyeongdo.

He finds out the name of the leader of the Sapa sect in my hometown and even points out the sect that is not even written down.

Damn it, of all things.

What can I do now that the name of the sect has been called?

Gu Jun-on closed his eyes tightly.

Then, the face of my son flashed before my eyes.

This is a portrait of my son smiling brightly while he was alive.

However, when Pastor Cheon Sa-mok occasionally visited his hometown, he heard that his son was a scumbag who beat and killed many people with a bright smile.

Yes, it's revenge.

Even if I die without being able to avenge my enemy, that woman's life will not be long.

If those who saw that woman's methods continue to fight for life and death, even if I fail, they will be waiting in the afterlife and laughing at that woman.

"Yes, I am Gu Jun-on. Do you remember the name Gu Young-jun?"

Qing answered, "I don't know."

"It was my son."

"okay."

Need I say more?

So, guys wearing the same uniforms come rushing out.

In Qing's view, except for the guy named Moonju, none of them seemed to have any particular fighting spirit.

Well, how much fighting spirit would there be in a situation where the son of the lord of the moon was dragged out because he died?

Qing laughed and raised her palm.

A white hand with transparent skin, the index finger stretched out slenderly and wiggled back and forth.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The most famous city in Jiangsu Province is Suzhou.

However, Suzhou is not the capital of Jiangsu Province.

It's just that the reputation of Jiangnan's entertainment district is so well-known that Suzhou is a more attractive travel destination than Chengdu for people from other regions anyway.

So where is the capital of Jiangsu Province?

It will be Nanjing, the very town known for having the dirtiest weather in Zhongyuan.

It's hot in summer.

It's not just hot, it's so humid that it's stifling.

On that topic, it's cold in winter.

If you hear that in certain cities in the northeastern provinces where the water freezes even in summer, you might frown and say, 'What's so cold about that?;

However, although it is one of the hottest cities in Zhongyuan, the water freezes in the winter, so the seasonal temperature difference makes it feel even colder.

Of course, this is in Zhongyuan.

If it had been about a year since Qing had seen it, would the weather have been this dirty?

Well, it wasn't something that the Korean people, who have similarly hot summers and much colder winters, would really feel.

Originally, the city of Seongdo was not the largest city in the provincial capital, but rather the oldest city.

Because the old city has a good location.

The fact that primitive people settled here in ancient times, when transportation and distribution were underdeveloped and even more so now, means that it was a location with a much greater geographical advantage than other cities.

And as is often the case in old cities, there was always at least one very old family that had settled there.

So what kind of families were there in Nanjing?

The Gongsun family, who committed no crime, were unjustly nitpicked and asked, 'Are you sure you're using that surname? How dare you use the emperor's surname?' These were the people who suffered injustice, having their surnames torn in half.

In fact, in Zhongyuan, when we say emperor, we were not referring to an emperor, but rather to the modern concept of a god.

If we were to go by the hometown of Qing, wouldn't it be a bit strange if the surnames were Jesus, Buddha, and Allah, so it turned into Je Susminsu, Bud Dhaminsu, and Al Lahminsu?

So, if I had to say, I guess it was worth cutting off the surname, but anyway.