\chapter{Chaotic Mess (2)}

The morale of the soldiers who crossed mountains and rivers was extremely high, that is, it pierced the sky.

First of all, the marching route is very flat.

A horse can cross mountains and rivers. What mountains and rivers were there on a well-trodden official road?

As I walked along the wide-open road, which was easy to walk on, I occasionally had the opportunity to admire the great beauty of the commanding officers, or more precisely, the Cheonhwa Sword, passing by.

However, the morale of the soldiers cannot be explained by this alone.

In the first place, military morale is greatly influenced by the reputation of the commander.

It was the Cheonhwa Sword that stood firm against its proud enemies, breaking, rolling, and cutting itself, yet ultimately achieving victory.

They were soldiers who shrugged their shoulders at an unrelated topic.

So, a smooth march.

Second city, term!

Linyi is the second largest megacity in Shandong Province after Jinan, the capital of Shandong Province.

If we look at the future according to the Qing Dynasty's hometown, Jinan will probably become a large city that can be counted on one hand on a continental scale, with its nearby coast, well-developed roads, and wide plains.

It is still only the second city after Jinan, probably because the national laws neglect navigation and it is far from the central plains, the center of the world.

Of course, this was a fact that Qing could not have known.

Not only did I not know, I also heard the name of the city called Imgi for the first time through Yun Yuanying.

Because the Qing's spiritual roots were from the barbarians of the border region.

In fact, it is considered a must-visit place for those who enjoy leisure in Zhongyuan.

Especially if you were interested in the text.

First of all, from this town, there is a giant of the Hundred Schools of Thought, Xun Zi of the Seongak Theory.

He is a Confucian giant who argued that humans were inherently incorrigible trash and must be corrected through education.

And Zhuge Liang, the undisputed leader of Zhongyuan, was from here.

And it doesn't stop there, oh my goodness!

Wang Xizhi, the pride of the Chinese and the very embodiment of Chinese calligraphy, is also from this town!

Great teacher. Greatest strategist. Best calligrapher.

This is the true mecca of liberal arts, producing all three!

So, it is a city visited by scholars of Zhongyuan and literati who were known to read literature to receive the spirit of the wise and wise man.

So when the term comes, the soldiers do what the soldiers do.

Setting up a military camp right at the garrison.

And the commander does what the commander does.

He was greeted by Lim Ki-Hyeon, a branch manager who had come out to greet him.

This is the commander's job, not to go out and play.

Politics is a series of actions that secure allies and bring enemies to neutrality through relationships.

Therefore, the commander in charge of the metropolitan area, Lim Ki-Hyeon, must maintain a smooth relationship with the branch in charge of the metropolitan area.

The branch manager thought a little differently.

Lim Ki-hyeon and Jang Qing-baek were the few people in the government with a conscience.

Because I lived without being ashamed of the name my parents gave me to become a man of integrity.

Of course, it is conscience based on the coffin's standards.

I can assure you that I never took bribes and wronged an innocent person.

But isn't the spirit of mutual assistance, where everyone benefits in return for their good deeds, a good thing that doesn't make anyone feel wronged?

Still, if you were a branch manager, you have to live in a large manor like a palace to have at least some dignity.

How can one build a huge estate with only a pittance in salary?

For the sake of the country, the dignity of the branch must be preserved so that subordinates will respect and follow it.

but!

In fact, even this alone can be said to be a conscience that can be counted among the works of high-ranking officials.

Anyway, Jang Qing-baek is feeling uneasy.

Why did you suddenly stop by and ask what was mine?

Anyway, since they were on different lines from the commander, there is nothing to gain from each other, and rather, when soldiers were stationed and training, they should be provided with food to eat along with military rations.

Wouldn't it be more like the city is being destroyed?

He puts the city's affairs before his own interests, which is truly the mindset of a noble official worthy of his name.

Besides, if you ask in advance, aren't you saying that it is purely a private use of the military for the personal advancement of the commander?

What? You're serving my precious mother?

Even so, what kind of tyranny is this during the busy farming season when the soldiers should be busy harvesting?

Especially when it comes to military affairs, it is a major matter for the country.

How can one not be offended when one is harming the country for personal gain?

So how does Jang Qing-baek express this discomfort?

Showing displeasure and pretending to be offended is something only the lowest of low would do.

The most important thing in politics is not to make enemies, so no matter how different the lines are, why would you grind your teeth and become enemies?

So, the place that Jang Qing-baek took Wang Ssang-ryong to for tea and conversation was Wang Xizhiji Palace.

Wang Xizhi's house is the birthplace of Wang Xizhi, the greatest scholar of Zhongyuan, and is now used as a sacred place for Confucian scholars and an academy.

In the style of Qing's hometown, it is an educational institution and museum.

Normally, if you were to entertain someone, you would offer them silk and delicacies and slowly try to get to know them, but why did you bring them to the prestigious Confucian Academy with its strong scent of paper and ink?

As a people who serve the emperor, remember the spirit of the Confucian scholars.

It was an elegant and solitary rebuke that made me feel ashamed and reflect.

Of course, Wang Shuanglong also understood him well.

How could a high-ranking official, even a commander, not understand a metaphor of this level?

But Wang Ssangryong is confident.

It is a matter of serving a mother who can live for a thousand years.

Isn't this the duty that a subject in charge of military affairs should naturally perform, rather than for personal glory?

So, Wang Ssangryong kept stabbing the branch leader in the ribs with his sharp eyes.

"Hey, Branch, what the hell is going on? Can't you take Myeongju and Jinmi to Madam right now?"

The branch snorts, "Huh?"

You said you were a precious mother, but you're just a martial artist?

I was wondering how beautiful she was because of all the fuss about her being the best in the world, and it turned out that she was a true beauty who couldn't hide her peerless beauty even with her puffy cheeks.

But even so, aren't you a martial artist?

Will a martial artist know loyalty?

They were scoundrels who do not understand the noble meaning of Confucianism or the Hundred Schools of Thought and simply act with force.

Will the martial artist know the immortality of the writing?

A sword only has a momentary power, but when it is buried in the ground, it rusts and decays.

However, the words remain eternal and were passed down as enlightenment that nurtures people, so the pen is more powerful than the sword and is the principle that creates the world.

So, Qing?

I look at the large scroll hanging in the old house.

'Etiquette is the most important part of the law and the foundation of everything.'

"Oh. Xunzi\footnote{Confucianism philosopher, lived around 310-238 BCE}."

"Do you know Xunzi?"

"Know Xunzi? How could this girl dare claiming to know the words of a giant? That's preposterous. I'm ashamed to admit it, but I studied under Master Tian for a short time, so I can at least understand few words."

Jang Qing-baek's bent back straightens.

"When you said Master Tian, were you referring to the Great Man Tian, the lecturer of the Hanlin Academy?"

"Yes. I am a disciple who lacks ability, but I serve the Master."

To say that one has served a Master and to say that one has a teacher were two completely different expressions.

All those who study at the Hanlin Academy say that they studied under the greatest master in the world, but in reality, it just meant they literally learned at the Hanlin Academy.

But what if you serve the Master?

This means that the teacher has a true relationship with the student, so in other words, they were called a disciple.

"Oh, how is the Great Man doing?"

Jang Qing-baek studied at the Hanlin Academy.

Although Confucianism had lost influence in the government, many of the children of high-ranking officials have studied in Hanlin Academy and held government posts.

Rather, they exchanged letters, lamenting that the power of the Confucian scholars was in danger, that the Confucian scholars should stick together and do something for their subjects, and that everyone was only filling their own stomachs.

So, how special must Jang Qing-baek be to meet his junior?

Do peaches still bloom like that in the Hanlin Academy front yard? Does the dining hall lady in front of it still do business? Is the bar to the east still bustling with scholars gathering together? When I think of those days, tears still well up in my eyes with longing, etc…

Wang Ssangryong's eyebrows twitched at Jang Qing-baek's sudden change in attitude.

This kid is here to study?

They say the quiet cat gets into the hut first, but you're trying to build a relationship like this while pretending to be noble?

"Ah. That’s right. Since you’ve come to Wang Xizhi’s residence, why don’t you leave a note before you go?"

"Writing?"

"It's like a commemoration. Since we've stepped foot into the birthplace of the divine penman, shouldn't we, as someone who holds a brush, offer a calligraphy as a token of respect?"

"Oh. Guestbook."

"Hey, were there any juniors over there!? A noble person wants to leave a calligraphy, so please prepare one for her!"

-The Young Lady is?

"She's a Confucian scholar who studied at the Hanlin Academy."

-Oh! Is that so? I'll get it ready right away!

Qing just thought of it as a souvenir to commemorate someone's visit to a tourist destination.

Actually, that was true.

When visiting Wang Xizhi's residence, it was natural for the literati to enjoy the scenery while writing a piece of calligraphy.

By the way, there were rumors that the paper is so expensive that the income must be enormous.

The price of that paper also varies greatly depending on the material and size, and the largest and best paper among them is called Sangjungsang.

When I came out, the paper was ready, and the large school hall was bustling with students.

That's only natural.

The scholars were wandering around outside, wondering how they could not take a peek when they heard that the most beautiful woman in the world had arrived.

But you even write in Korean on the Hanrimwon bachelor's degree?

How can I put up with this?

So, among all the scholars gathered, Qing looks down at a large piece of paper large enough to comfortably accommodate one person.

What is this? The guestbook is a bit big.

Well, can I just write it in big letters?

After thinking for a moment,

Because Xunzi said she was from this neighborhood?

He lifted a large brush, dabbed it with ink, and with a single stroke, four letters the size of a door were soon imprinted on the paper.

麻中之蓬. Ma Zhong Zhi Peng.

It is a four-character idiom meaning 'mugwort in the midst of hemp.'

It means that even a crooked and drooping mugwort will grow straight up if planted among straight-growing hemp plants, following the others.

This is Xunzi's saying that if you hang out with good people, they will naturally become good people too.

It was the wish of a giant who believed in the potential of humans, that humans were trash from birth but can be reformed through education.

And then the school exploded.

"What great writing is this!"

"Each stroke carries a weight of a thousand pounds, so it is like an ocean that cannot be invaded or harmed!"

"I can’t believe such writing exists in the world!?"

"Oh my god!" "Oh my god!" "Oh my god……!"

"Wait! Don't move! It's dusty! Bring the grass! Quickly! We have to walk this way to preserve it!"

Jang Qing-baek, the branch manager, was deeply conflicted.

\textit{Can I take this?}

\textit{If you hang it in your office and look at it whenever you feel lonely, all the amusements in the world will be useless, and it is the ultimate calligraphy that you will never tire of looking at.}

\textit{Everyone who comes will be amazed and amazed. Isn't this a sacred object that adds more dignity to an army than ten thousand soldiers with just one piece of writing?}

\textit{And since the prestige of the branch is the prestige of the government, isn't taking care of it the way to show true loyalty?}

At the same time, he thought he understood why the Scholar of Study had insisted on having a woman as his disciple.

With such handwriting, how could he not be taken as a disciple, even if he were a great scholar rather than a poet?

"You were already a great giant."

"Yes?"

"This old man is shameful."

In this case, wouldn't it be the case that even that greedy commander treated him with the utmost respect and mobilized his troops?

How could there be such a shameful thing in the world if you came out and said you were lecturing me without even knowing it?

"Aren't you ready for dinner yet? Since you've come to the royal palace, it's only natural that you should be invited to the Nangya Pavilion and admire the breathtaking scenery."

A smile spread across Qing's face.

Wow, they're giving me food!