\chapter{Chaotic Mess (8)}

The crowd hopes that the next challenger will appear quickly and that the life-or-death battle will continue.

He is a challenger, not an avenger.

Originally, a challenge was an act of pushing out someone who was already in the same position, so it wasn't an act of trying to make a decision against someone of a higher rank.

This is the perception of the crowd.

But would you take revenge just to entertain the onlookers?

Those who say they were seeking revenge may weigh this and that and click their tongues, saying, "I will really seek revenge."

If you really have a deep grudge, shouldn't you just jump in without hesitation?

It is a characteristic of thoughtless people, and those who were so thoughtless and blinded by anger all died in the Yubanghyeon Arena.

A truly dangerous grudge is an unavoidable dagger that stabs at the enemy at the most vulnerable moment, when they show their weakness.

Rather, it can be said that only those who endure good times and weigh the pros and cons were left - the true avengers and truly dangerous ones.

It's not time yet.

I'll see how long you can keep acting all cool and arrogant.

Of course, Qingdo knows that fact.

Even though they don't come forward, wouldn't those guys with bloodshot eyes and red eyes stare at you with murderous intent?

I'm always on guard because there were guys who might interfere during the duel.

But you can't avoid it forever.

In fact, the more life-or-death decisions were made, the more disadvantaged Qing becomes.

Because the Qing's enemies were observing the Qing.

What method do you use and how?

What hand do you use most often, what direction do you prefer when avoiding, what were your habits, and how many secrets do you still have hidden?

All the guys who were going to come out because they were angry have come out.

They were blatantly observing the remaining ones to analyze them one by one and find a way to win, so the more they fight, the more they were being seen through.

So, in a way, Qing is pushing himself to the extreme.

In other words, you can just pay it back!

The unmanned aerial vehicle of the climax and the scenery were as different as the huge wall that Qing saw in his mind.

Do you dare to analyze the transcendent, transcendent, transcendent, transcendent purity?

If you want to do it, try as much as you want.

Anyway, if you get into a situation like this, all the information will be useless and wasted effort.

So, I need to get into the flower market quickly.

Miss, it's like a sneeze that's really stuck in the tip of your nose, like a booger, something, ha, ha.

If I could just vomit out the cool air, I think I could reach the realm of Hwagyeong, but I feel like I'm missing something, some kind of decisive stimulus.

As if I wanted to eat something.

Just the right amount of salty? Rich enough to melt on your tongue? Sweet enough, but not so sweet that it makes your mouth water? Spicy and tangy enough to make you let out a groan without realizing it?

Anyway, it's like when you're eating a lot of delicious food but you can't remember what it is.

It's so frustrating.

So, I guess you're just trying out different things.

But that's just a life-or-death decision.

So, let's start with what we can do now.

Qing, who had been wearing a bloody helmet, sat quietly in front of the sunshade table again and looked back on the battle.

This time, there was a problem with the net itself.

Why couldn't you avoid it?

That's because the trajectory of the Neungpa Mibo was discovered.

A net was spread across the escape point of the Nungpa Mibo, so it was like jumping into a trap with one's own feet.

How did you know where I would show up?

Somehow, I write about unknown experiences or feelings that have been ingrained in my brain and body through shortcuts.

However, by stepping on the Bagua, the world was distorted into a formation, and the field of vision overlapped and expanded, so even when Qing himself wrote it, it was extremely confusing and complicated.

Were there any such people as experts in formation?

Of course, from the perspective of those who were watching the moment when Qing steps on the Neungpa Mibo, he and his eight clones fly, crawl, and jump in dazzling movements and scatter in all directions, but he himself has no way of feeling what his appearance is like.

So, um, I don't know.

I just know that it's not an invincible escape.

Why, even back home, when playing video games, didn't they predict the so-called "blink" teleportation technique?

Since they've shown it to you several times, you probably spread out your nets in several places, thinking that it will appear roughly here and there.

It was the moment when the myth of Neungpa Mibo's invincibility, which I had believed in like iron, was shattered.

No, you're saying it's the best dharma, the invincible divine skill?

Is it really a divine skill that can be seen through by such a miscellaneous sapphire?

Shouldn't the purple border be removed?

If anyone heard this, it would be heartbreaking.

That pig-like bitch is so greedy, where in the world can you find a perfect martial arts technique? There were people all over the world who would risk their lives to attack her if they saw her, but she's so full of stomachs.

Qing, who had been grumbling, suddenly comes to a realization.

Anyway, come to think of it, it's a martial art from a ruined sect.

If Neungpa Mibo was truly invincible, everyone would have been alive and well. Why would they have failed?

If the sect members in the afterlife heard this, they wouldn't really have anything to say.

The martial arts of the four sects were all divine arts that transcended the laws of human life.

But the disciples were ultimately just mere humans, so wouldn't it be a sect that split among the four disciples, fought each other, and ended up killing each other before disappearing?

So, rather than making excuses like "there was an internal conflict, people killed each other, and it all went to hell," it's much better to just say that there was a flaw in the martial arts.

It seems that Neungpa Mibo is not a good person.

It's a good thing I found out after dealing with easy guys, but if the Hwagyeong master had predicted it and hit me with something like a Gyeokjangjang, my back would have been broken.

Then what should I do?

At what moment should I write so that the enemy doesn't predict it, and even if they do predict it, will there be a situation where I have no choice but to let it go?

In any case, each and every one of them was a life-or-death experience for Qing.

As the enemies analyze Qing, Qing is also desperate to erase its own weaknesses.

The invisible battle between the spear and shield ended without being seen, and today's duel also ended.

I see it's been written in this neighborhood too.

This is not a good trend, in Qing's opinion.

Because it will be difficult if you push yourself too hard later.

Is there any way to make them jump in?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Jiangnan!

For people in Zhongyuan, Jiangnan is a term that combines Suzhou and Hangzhou, and is also recognized by everyone as the best entertainment district in Zhongyuan.

This is an unusual situation for a Chinese person.

The love of the people of Zhongyuan for their hometown is so special that it is almost extreme.

It was so common for people to brag about their hometowns, cities, and provinces that it was considered a taboo to bring up carelessly at social gatherings.

In this atmosphere, it is a great thing that all people in Zhongyuan recognize that Jiangnan is the best entertainment district in Zhongyuan.

'Food? Our neighborhood is the best when it comes to cooking.'

'Academics? Literature, too, is the best in our neighborhood.'

'History? Our neighborhood has the best history, too.'

'Scenery? Our neighborhood has the best scenery.'

'Geography? Our neighborhood is the best in geography too.'

'Entertainment? Oh, that's Jiangnan.'

'But you know, our neighborhood is only second best to Jiangnan.'

This was the prestige of Jangnan as an entertainment district.

And also, Gangnam is a city of writers.

When you think of a writer, you think of the scent of ink and paper, but in fact, when you think of a writer from Gangnam, it doesn't sound so good.

This is because the word 'literati' is used to describe the vagabonds who sit around, drink alcohol every day, and play with gisaengs, while reciting tales of the past and the future.

No wonder the interest of Jiangnan writers has always been in beauties, past and present.

So, that's what we always talk about when we get together.

Who is the most beautiful woman in the world?

Who is the most beautiful woman of all time?

I heard that the new gisaeng who came to Wolhwaru this time is really beautiful.

What? Then this isn't the time.

Who were we? Aren't we the literary men of Gangnam?

Let's make a bet to see who can raise their head first.

When it comes to Gangnam's gisaeng, this one is also recognized as the best in Jungwon, so her pride is also sky-high.

Even prostitutes who sold their bodies were judged based on the qualifications of the customers they accepted.

If even prostitutes were like this, how much more so must the young women who do not sell their bodies be?

They say that gently melting them into bed with words or tricks is called lifting their heads, so let's bet on who will be the first to seduce them.

These guys were exactly what the expression "Yeomisae" (a type of "crazy bastard"), used in the Qing hometown expression, means.

So, what is the biggest concern of Gangnam writers these days?

The beauty who is staying at the Soju Taeho Inspection Center.

It was Xue-i-ri, whom the literati called Xue-seon-nyeo and the martial arts people called Bing-Xue-hwa.

Xue-i-ri settled in the Taeho Inspection Center in Soju as part of a local tour of the prestigious post-graduate index conducted last fall.

The deadline is the end of winter.

But winter is long gone, spring and summer have passed, and fall has come again, so why do I still sit down to drink soju?

Well, because I gave you food.

Not just any rice, but good rice.

They give you pocket money there, you get a seat in the best guest house, and you can even spar.

Xue-i-ri's impression was always cold and arrogant, but what was her true state?

Even when buying a snack, I fumble with my empty pockets, debating whether to eat it or not. I want to eat it, but it's too expensive. My shoes were worn out, and I need to buy a new pair, but I wish I could find a clean pair that someone left behind somewhere. But I keep thinking, "Isn't there a Yongbong branch meeting today? I'll get some delicious food there." It's the very definition of a miserable feeling.

So, Taeho Inspection is a place that Xue-i-ri likes because it provides her with good food, a nice room, and a lot of pocket money.

Even if you ask for things like uniforms and shoes, wouldn't they be able to give them to you?

Besides, since you just have to settle in the sect, it's not like you're indebted to anyone.

So eat well, take care of yourself, and practice again.

Open your eyes, do some exercise, eat some food, do some exercise, eat some food, move your body, practice some, eat some food, do some exercise, eat some snacks you brought from a restaurant, do some exercise, and if you go to bed late, you have to start over again.

Even with such a harsh diet, sometimes I crave something more luxurious than the food provided by Taeho Inspection.

Then, Xue-i-ri quietly came out of the guest room and wandered outside.

Then, some people come running and ask me to go eat something delicious.

Of course I've heard the name, but I have no reason to remember it and no intention of remembering it, so I don't know the name and just say so-and-so.

For this reason, Taeho Inspection is actually starting to want him to go home.

It was a great help just to have them with you when the Sapas started acting suspiciously, but that only lasted for a day or two.

It only takes a day or two to be captivated by the splendid beauty of Wulin.

The disciples just roll their eyes, putting their training on the back burner, trying to force it in somehow.

The literati of Gangnam, who should be in Hangzhou, have settled down in Suzhou, so the rumor that BingXuehwa, who occasionally goes out for a walk, is weak in cooking has spread widely.

But you still have to give them allowance.

No, you eat, sleep, and wear clothes without spending a single penny, so what on earth do you do with your allowance?

The correct answer is appreciation.

Before going to bed, Xue-i-ri's only expression of emotion was to open the front door and look into the dazzling golden light, smiling faintly.

To be exact, rather than thinking of the weight of the gold, I thought of someone eating it happily, and decided that this time, I should buy it instead of getting it.

Today, too, Xue-i-ri left the guest room, craving hot, thick soup.

however?

"Oh, Miss Xue. Did you hear the news?"

"no."

"Oh, I haven’t even told you what the news is yet."

"Should I know?"

"That’s not true."

"Yes. Then."

A very cold wind is blowing.

With this, I can't help but think that Taeho Inspection should slowly turn back.

But he is not a disciple of Taeho Inspection.

"No, no, could you please wait a moment? I was wondering if you, Young Lady, were acquainted with the Heavenly Blossom Sword."

Xue-i-ri stands tall in front of him.

"Why, Miss Ximen?"

"Ah. You didn't hear. The whole Soju is buzzing with that story. Heavenly Blossom Sword is leading his troops and coming this way... ..."

Taeho Inspection also stops midway.

It was because it was the first time I saw BingXuehwa's face with a faint smile.

The moment when you truly fall in love anew-

"When?"

"yes?"

"When will Miss Ximen arrive?"

Taeho Inspector was about to answer, but then he said, "Huh?"

Are you not really interested in the part about Heavenly Blossom Sword leading the army, and were you just curious about when he will arrive?

That's actually true.

What does it matter whether the Qing led an army or a band of bandits or whether they led the Japanese pirates on a plundering expedition?

They said they were coming this way.

"Well, I'm not sure if we'll be able to get there. They say the enemies of the Cheonhwa Sword were following along with the military, seeking redress. "Where were you going, Miss Xue?!"

Xue-i-ri turns around and runs away before she can even finish speaking.

With the ice and snow disappearing in a flash, Taeho's swordsmanship is left alone. What the heck? But that smile... wow, was that a smile?

Taeho Inspectorate scratched his head, but didn't he still enjoy the view?

It was a breathtaking view that would be etched in my mind for the rest of my life, so I didn't lose anything.

So he turns around and heads to the disciples' quarters.

Then, there was a moment when I turned the corner.

"Where were you now?"

It's a sudden appearance of a snow flower.

Carrying a large backpack wrapped in a thin blanket.

"Huh, Miss Xue? What’s going on all of a sudden?"

"Miss Ximen. Where were you?"

"He said he would stop by the breasts, the uterus, the perineum, and the uterus in that order, and then come to Soju. If you go back in time-"

Xue-i-ri jumped up again before he could finish speaking and climbed over the checkpoint wall.

Taeho Inspector, who was left alone, was scratching his head.

What was it?
