\chapter{Chaotic Mess (11)}

Gong Sun-Yaoyi is very popular these days.

The Gongsun family is becoming more and more prosperous.

It's been a year since the martial arts competition ended.

There were several new warehouses, and the walls had to be knocked down twice to expand the estate.

There were also many new warriors.

Although accidents did happen often, a powerful family has the ability to ignore such incidents as if they never happened.

Of course, it was because the ten great martial arts masters who were truly recognized were included in that framework, but more than that, the speed of development was quite different before and after a woman entered the family.

"Sister, hehe, can you hold this for me?"

Eyes that were slit open, pupils the size of soybeans, lips that were bright red as if smeared with blood, and teeth that gave off a sharp impression.

A woman with a very evil look on her face hands me a tray with a suspicious smile.

Somehow, the teacup on the tray seemed to be poisoned, as if a black line was blooming around the woman.

"Ah. Thank you. Um, Little Sister."

"Thank you, though. Hehe. Too much of anything is bad, so what if you end up hurting yourself? What would happen if you did? Hehe."

It seems like a veiled threat.

But she knew that's not what she meant.

Lady Sima Ling was originally like this.

His younger brother, Gong Sun-Tianri had a formal wedding with Sima Ling, the youngest daughter of the Sima family, last spring.

For a daughter from a prestigious family, she is a rather plain woman.

Personally and objectively, it is a pity that Gong Sun-Tianri, who was a very good person, was getting married.

But Sima Ling was a good woman.

Not only was she kind, but she was also capable, and even before her marriage, she was involved in all kinds of business as the prospective mistress of the Gongsun family, and she was also a talented woman who took control of the Nanjing business world in one fell swoop.

When you say "Olke" that Gong Sun-Yaoyi knows, doesn't it give off a feeling of something a bit wicked? Something repulsive and vicious?

Why is there nothing that matches other than appearance?

In fact, Sima Ling is also thinking similarly.

They say that this family was so desperate to get their surname back that their mind was already racing. How anxious must they have been to head to their in-laws' house before even getting married?

Besides, Gong Sun-Tianri's appearance was not ordinary.

But Gong Sun-Tianri was a good husband.

Mother, father, and all the family members were polite (although a bit impersonal), and the keys to the warehouse were already flying in before the wedding, so isn't this a symbol of the hostess?

And she was worried that her new sister-in-law would be bullied because he said that her sibling relationship was close, but guess what?

Since Gong Sun-Yaoyi were naive, if you don't take care of her, she might had fall while swinging her swords.

And yet, she's always awkward and struggling, um, what is it? Isn't that cute?

Anyway, Sima Ling is very satisfied.

It's much better now that she's the head of a household than when she was being shadowed by his father, older brother, older sister, and younger siblings in Sima family, where everyone was living their lives with their own tastes.

"But is it okay for you to stay like this? I heard that the Heavenly Blossom Sword is currently engaged in a life-or-death battle with her enemies. Aren't you her best friend? Shouldn't you be going to help?"

"Huh? What does that mean?"

Sima Ling tells her the story.

Gong Sun-Yaoyi, who is stuck in the training hall all day, has no way of knowing the news outside.

After the martial arts competition, no one forced her to practice, but it was a training she chose on her own.

Now that the family has reached the top ten, the next thing they need is a peerless master who will make a name for themself.

And it's also because she didn't know how to live life any other way.

"I-I have to go help right now…!"

"Haha, I knew you'd do that. Now, I've already packed her bags. Take them and go."

To others, she would appear to be a mean sister-in-law who kicked out the family heir, a thorn in her side, and an evil mistress who has taken over the family.

"Yeah. Thank you, little sister."

"You're welcome. Hehe, if you're grateful, can you arrange a meeting with Heavenly Blossom Sword? I wonder what kind of person she is. Hehe."

It's not a dirty scheme, but her pure desire to see the great swordsman of Heavenly Blossom Sword whom she truly admire.

To the female aspiring martial artists of Wulin and the youngest female artists of the time, Heavenly Blossom Sword is the person they want to meet as the next best female martial artist.

"Hmm. I’ll try."

"Oh, you have to have your clothes washed at each guesthouse you visit? Since you have four spare sets of underwear, you'll need at least two sets left. And the rice balls were a one-day supply and won't last long, so you'll need to eat them quickly, right?"

"Huh? Yes……."

"And I’ve added fifty silver coins and a few more in the form of vouchers. I put them in with my own money, so feel free to use them as much as you want, or rather, use them all up if you can. I put them in a waterproof pouch, but the vouchers may get wet, so be careful. Always carry the silver coins in small portions in your pocket. Pickpockets were no ordinary people, so even martial artists can be snatched away if they let their guard down. And… be careful of old people, women, and children… even if a suspicious person asks for help… be careful of holding grudges, but if you do, it’s certain…"

\textit{Why do you keep nagging me after telling me to leave?}

Gong Sun-Yaoyi was sweating profusely, but she couldn't refuse.

Just quietly listen to the nagging.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A move of the Emperor's Sword style that unfolds on the Unwoldo.

It was the blade of the Unwoldo that drew the fastest and most accurate trajectory of all possibilities.

The Black Tiger Gate lord was killed with a single stroke of the sword.

He rushed in and was split in half, his upper body flying far away and his lower body falling flat on his face, all messily spilling out.

In an instant, the new blue form swells greatly.

Enemies, crowds, and enemies all look to Qing and see a giant reaching to the end of the sky.

Just stand still and rule the world.

But Qing's expression is indifferent.

What meaning could the death of a mere scribe have to the emperor?

What Qing sees is not the enemy, but the world.

Looking down from heaven to earth, it is the gaze of the emperor who moves a million soldiers on horseback.

Qing takes a peek into the mental image contained in the Emperor's sword.

The emperor is alone and noble, without enemies or allies, he simply exists and rules over all people.

So the emperor stretches out his hand.

A careless attitude that only aims the tip of the sword.

However, the Black Tiger Warriors feel a fear as if a blade is falling on their necks.

Aaaah, I try to shake it off with a scream like a scream, but I rush in and unknowingly go into battle knowing that I will lose.

Because it has to be that way somehow.

Black Tiger Gate, destruction.

Blood drips from the tip of the sword.

Still, the Moon Blade is on the moderate side.

Behind it, on the opposite end of the spear, hanging from the iron hammer were human skin, pale brains, and pieces of internal organs, making for a gruesome sight.

With all the main warriors dead, the destruction of the clan was already certain.

According to the law of the Black Sword, the weak were destined to be torn to pieces, and in fact, isn't it the nature of the Sect members to run away with the sect's assets before being torn to pieces?

"Then."

In the quiet space, only Qing's voice was heard.

The sound of saliva being swallowed.

What follows is something everyone knows.

"Next person."

As always, Qing throws out a word.

The enemies were just perplexed.

'When did you learn to use the Crescent Blade?'

'Wouldn't this make me go out?'

But among them, there were many who nodded their heads solemnly.

'That thing must be killed now.'

If they missed this moment, she'd become a giant that cannot be defeated for the rest of their life.

So, the unmanned people come forward and say their names.

But what about that number?

"How can nine Peak Realm appear at the same time?"

"Isn’t it common sense in martial arts that one warrior in the Transcendent Realm can fight three warriors in the Peak Realm?"

Qing was speechless.

\textit{No, since when did I agree to that logic?}

\textit{Come to think of it, it might be because of the guys who came in droves the other day.}

At that time, there were a lot of different people, so she just accepted it because the tangled mess of people was what Qing was most confident in.

Qing hesitated for a moment.

\textit{Should I send the signal?}

\textit{Even if I'm the most Transcending (omitted) Transcedent, can I handle nine Peaks?}

\textit{Can I stop nine lines of swordsmanship?}

That was when.

"Wait a minute! Does this make any sense!?"

A voice of someone nagging.

It's also a very familiar voice.

A woman suddenly appears and heads to the seat next to Qing.

Although she was small and wore a hat that covered her face, there was no way Qing wouldn't recognize her.

"Huh? What are you doing here?"

"I can't live seeing you like this. What kind of grudge is this? What kind of enemy is this? It's not like you're putting on a show."

"Hmm. Not really..., um, let’s talk later-"

"You don’t like it?"

The little girl rolled her eyes and immediately shouts.

"Since this is a place to resolve grudges, I, as a close friend of Lady Ximen, will also join in! The girl's realm is still in its Mid-Peak, so if there's anyone in the same realm, either step forward and join those vile bastards or not!"

"Wait, don’t do that-"

"Is it okay?"

Then, more young people appear in line with that.

They stood shoulder-to-shoulder next to Qing.

"I, too, will assist Heavenly Blossom Sword. My realm is Peak, Mid-Stage. If you wish to match the numbers, you may come out now."

"I'm the same. Transcendent Realm, Early-Stage."

The big, burly man spoke with an unbecoming politeness, and someone who looked handsome just by looking at his jawline under his hat added briefly.

"Huh, what is this? When did San reach Transcendent?"

"Hmph. There’s someone who’s been bragging about reaching Transcendent first."

"Sister, aren’t you happy to see me?"

"Huh? I'm glad to see you too, Zhuge. I'm grateful for your kindness, but-"

"If you're going to suffer, wouldn't we also lose the leader of the Half-Sword Double-Saber Society and have to seek revenge? Originally, it was called Bangmi Doujeong. Oh, do you know Bangmi Doujeong? It means, if something small is about to grow bigger, don't just watch it grow bigger, but eliminate it before it happens. This happened when Emperor Zhang of the Eastern Han Dynasty died and his young son, Emperor Hua, inherited the throne. The Du family, with their dreamlike power, were treated with great respect wherever they went, and civil and military officials demanded their approval, so they must have felt like emperors. But here, this man named Jeong Hong—"

"No, it's not about that. What’s going on? How'd you get here?"

"Well, you didn't come by boat, did you? Originally, Hoein was the largest salt warehouse in Zhongyuan, and especially so, with the former imperial palace located in Kaifeng, it's directly connected by a canal. So, by boat, it's difficult to go upstream, but easy to get down. So, if you catch a boat on the Grand Canal, it's quick—oh, this isn't a canal waterway, it's a speedboat. What's the difference between the two?"

"No, I said it's not about that."

Qing's eyebrows twitched.

The Zhuge in my memory was quite talkative.

But it seems that that was also just an embellishment of memories.

Yeah, there used to be this much talk.

"Um. Everyone, thank you for coming, but for now, would you like to go to the barracks and wait? I'll take care of it right away and be on my way."

"You don’t like it?"

"It’s dangerous here-"

"Then what about us? Are we just going to watch you in danger by yourself?"

Tang Lan-ah responds by lighting up her twin flames.

She was speechless at that.

So what should she say here?

'You guys were so weak.'

'If I also have protect you, won't it be harder for me?'

Even if Qing was good at being rude, it was not something she should say carelessly.