\chapter{Chaotic Mess (13)}

Zhuge Lixian's role was to protect Tang Lan-Ah.

Zhuge Lixian also had no complaints.

First of all, it was true that he lacked the skills to stand up to Transcedent.

And wouldn't the bloodline of the Zhuge family have a great advantage in observing the battlefield from the rear and adjusting it in a more advantageous direction?

(That's what Zhuge Lixian thinks.)

So, he should stepped back, adjusted the overall formation, and pursued a more advantageous and complete victory.

Zhuge Lixian, who thought like that, was currently committing a very serious dereliction of duty.

Because the tuning was nothing, he just stood there dumbfounded.

The arm of the sturdy giant Zhuge Lixian was as thick as Tang Lan-Ah's waist, so just by standing there like that, he gave off an intimidating vibe and served as cover for Tang Lan-Ah.

Because she was a busy kid who came and went out of his back like a squirrel scurrying in the bushes.

So why did Zhuge Lixian lost his cool?

Well, how can one came to one's senses after seeing the movements of that brave Unwoldo?

Wol-do is basically the most serious of serious weapons.

In the first place, if you can't use your internal energy to supplement your strength, it can't function as a weapon.

What practical use would a weapon have if you swing it a couple of times and then get tired and out of breath?

So, it is a weapon that only the most elite soldiers, who have dedicated their lives to the military and learned the martial arts of the Imperial Army, can use.

What the heck is that beautiful iron hammer there!

Zhuge Lixian, a weight expert, looked at the shine and saw that it was made of solid steel, not plated. With that much mass, it would weigh about ten pounds.

And judging by the length of the iron bar and the blade, it must be about fifteen geun, and a total of twenty-five geun, a heavy weapon that has never existed in the world.

And there was a woman swinging that heavy lump of iron as lightly as a willow branch.

The weight is roughly 25 pounds, but since the center of gravity is concentrated at both ends, it would actually weigh much more when swung.

The sharp angle of the Qing's crescent sword repels the sharp blades that strike at you.

This is a phenomenon in which the enemy's locked posture is opened due to the overwhelming difference in the mass of the weapon.

Then, the iron weight shakes and splits into three, and the terrified enemy, not daring to face it, rolls on the ground in shock.

You're saying that weapon will show you the magic of pleasure and joy?

If you lifted that much weight, you will inevitably be swayed by the weapon.

This is precisely why the martial arts technique of using a heavy weapon rotates in a circle. It is the principle of adding strength to what is lacking through muscle strength by drawing a circle.

But what the hell is that god?

If you use a blade, the weight is close to your fist, so your body doesn't tilt, and if you use a weight, the blade is close, so you don't stagger.

A method to completely suppress a serious illness with force, a divine power that everyone knows but cannot do!

Every move is the essence of power that transcends human limits. Just how much strength and power is needed?

Even jumping up and down.

Qing flies with his Nang-A-Eon-Wol-Do and bang! He ends up hitting the shoulder of a warrior.

The shoulder that was hit by the iron hammer exploded, and the arm fell off and rolled on the floor.

How on earth could you hit someone with a blunt object and get such results? This is truly amazing, Sister, you were amazing, this younger brother, I am truly touched. I saw a new world today.

It cannot be explained by the power of internal energy.

This is the pure strength of humanity itself!

No, it is a strength not granted to humans.

How could a person have that kind of strength in the first place?

But perhaps, the limits were different for each and every person.

So, just as General Xiang Yu did in the past, perhaps this person is the possessor of the most beautiful power among all the people in the world, no, among all the people of the past and present!

Suddenly, a scene flashes through Zhuge Lixian's mind.

The training ground at that time.

A two hundred and fifty pound weight that someone had lifted and moved.

A scene where a thing was lifted high and dropped, and a hole was dug and it was rolling around.

And Sister hurt her shoulder.

As if she were lifting something heavy with one hand and overusing it and got hurt.

Zhuge Lixian's eyes followed Qing.

A power that truly defies the laws of humanity!

In Zhuge Lixian's short life, this was by far the most beautiful scene.

Meanwhile, in Wulin, the level of a martial artist who uses poison is raised halfway.

In fact, in Wulin, poison is a dangerous but ambiguous technique.

In the Qing's homeland, if you were poisoned, you should go straight to the hospital and lie down in the emergency room. If you bring the poison that caused it or the corpse of the poisonous creature in question (if it is dead, this does not mean kill it), that is, if you can accurately tell the type of poison, the survival rate will go up considerably, so it is good to remember.

In any case, in the Qing's homeland, poison is a terrifying weapon that must be dealt with without the help of medicine, and even with the help of that sharp medical power, there were deadly poisons such as the deer horn mushroom nuclear fission black tea that you can never survive.

This is why you have to be careful of the shims.

But what about this pseudo-Zhongyuan, where people fly around in the mysterious energy of the universe, but in a primitive society that is equally uncivilized?

When your internal energy reaches a certain level, you can delay by inducing the poison in your body.

If you give it enough time, it can be removed on its own.

A relatively low-level martial artist gathers poison at the tip of his fingers and squeezes it out, while a high-level martial artist burns away the poison as if his own body were an incinerator.

What about bottom feeders? Well, they just had to die.

Or you can bow politely and ask, 'Hehe, teacher, mayhaps do you have any antidote?'

Even if you become a Hwagyeong's unmanned weapon, you can burn away the poison that has penetrated in an instant and become healthy, and you can even suppress and delay the poison while fighting.

There the toxicity of the poison is at its maximum.

This is because as the level increases, the poison does not increase in rank to become a plus one plus two, or a special, very special poison, or an incredibly special unique poison.

For this reason, as the level increases, the warrior who uses poisonous techniques becomes weaker and weaker.

Nevertheless, in Wulin, the level of these vile poisoners is recognized and raised to about half.

Because, in a fight between many and many, the influence of a master of ranged attacks is enormous.

Nine, no, two of them jumped out early, so the Seven Avengers were going to be a total slaughter.

To be exact, they weren't dying, they're as good as dead.

The poison is spreading, and to survive, I need to quickly defeat the enemies, sit cross-legged, and expel the poison, but that ghostly, dog-like, poisonous bitch quietly retreats and as I try to expel the poison, she starts spewing out her secret energy like a ghost.

It's not even just poison.

It's a type that spreads secretly, stiffening muscles and making breathing difficult. It's not painful, so it's not an insidious thing that's easy to drive out even if you focus and concentrate properly.

So, the enemy appealers had no choice but to die one by one and roll around on the floor.

Finally, there were only two people left.

As the evil Heavenly Blossom Sword and the unidentified handsome man slowly close the distance, the two revenge seekers exchange glances.

Strong eyes filled with solemnity.

As if to say, 'If we die, why should we just die alone?', as if to say, 'Shouldn’t we take out at least one of them?'

The two drones looked at each other and nodded.

And as if they were matching the sum, they unfold their final move at the same time-

In that moment, their hearts were in sync.

I need to throw that kid and run away.

"Get out of the way!" "Can’t you get out of the way?"

The two of them turned their backs at the same time and ran away.

The two drones, standing shoulder to shoulder, look at each other and cannot hide their bewildered expressions.

'No, you too?'

'If you run away, who's going to held off those guys?'

Of course, there is no one to hold onto.

But both of them had something to believe in.

Since there were spectators watching, once they get far away, they won't be able to recklessly fire their weapons or use their attack skills.

If that bitch seemed to be getting a little farther away, wasn't it a tactic to aim for the leg so that even if it missed, it wouldn't hit the onlookers and would end up on the ground?

So, first, keep your distance, and when you get close to the crowd, you won't be able to fire your cannon recklessly for fear of missing.

And it actually worked.

"Huh."

Looking at the backs of the two running away with Qing's back turned.

Oh, well, if I had lost face, I could have run away.

Why didn't I think of that?

Qing raises his internal energy, then hesitates, puts it down, and kicks the ground.

If the crowd is close and you throw the Tathagata Spirit and they dodge, it will be a massacre of civilians.

But since I've been stung, I won't be able to go far. For now, I'll chase after him and, oh, this is good timing. I'll use the excuse of desertion to end the duel.

Qing takes one step, two steps, and-

"A beast-lover who would shackle a male dog dares to command me! The Buddha's boundless compassion teaches the subject!"

The left drone falls with a loud scream.

Bloody marks clearly visible on the mangled body.

In the palm of the Buddha's hand, who is truly merciful, the Buddha in Tibet seemed a bit extreme.

And the drone on the right changes direction and flies into the sky at the same speed it was running at.

When I saw Qing's head facing straight at me, I absentmindedly reached out and five long fingers stopped his head in its tracks.

Behind him, Zhuge Lixian stared intently, but Qing's spatial awareness is not that wide, and even if he were close, the extent of his stare would be such that even Tian Yuxue, let alone Qing, would not be able to tell.

Even if he knew, he guessed he thought his pride as a muscular man was hurt.

As Qing, unaware of the circumstances, looked at the turning point, he saw the ladder itself, a fat Povidone, snorting and shaking its belly.

In fact, if you can break through the crowd and get a special seat in the front row, you were not an ordinary person.

Even among the unmanned ones, they were the only ones who could do it, so running away to find a way to survive was not a very wise decision.

So two escaped, six died, and one was killed by a bystander while trying to escape.

However, the audience's reaction was a bit...

Hmm. I had a good time.

'Is this something we should be cheering for?'

'But isn’t it still four against seven? And isn’t there only one more Transcendent expert added to the Heavenly Blossom Sword side?"

'But if you use poison, well, actually, even if all nine of them had attacked, wouldn't more than half of them have been affected? is that right?'

'Hmm.'

If even the audience is like this, how must the enemies feel?

One to nine, they didn't mind if Heavenly Blossom Sword died.

Or even better.

The time has finally come for them to step forward.

But didn't the friendly protesters who suddenly barged in and started a ruckus?

So they're gritting their teeth and they're not going to let those bastards sit still.

No, they'll kill those bastards first!

Then, how would that Heavenly Blossom Sword feel? If her close friends, who were willing to stand up for her, died because of her—-

"What the heck, we won, why is this atmosphere like this? Ha! I knew this would happen. Yeah, I'm just being cowardly and using poison, huh? If you're dissatisfied, then come at me! The Tang Clan doesn't shy away from a challenge!"

--she'd must be really sad, but it had to be that damn bitch from the Sichuan's Tang Clan. What a shame.

The enemies just switched target.

The Tang Clan girl were a bit too much for them.

If you had to pick one force in Wulin that you would most want to avoid, who would it be?

Well, no matter who you asked, the answer is self-evident.

Shaolin Temple!

If you asked to pick a second one, this is also an obvious answer.

It was Sichuan's Tang Clan!

Those crazy guys who use poison, those poisonous bastards who will cut off a limb if they just get poked once.

That's why the enemies' eyes were on the handsome man.

"Peng Daesan of Peng Family."

In an instant, the screams of women going 'Kyaaaaa!!!' filled the whole city.

"Jade Kirin!" "The most handsome man in the world!" "I love you, oh my!!!" "Jade Kirin, my older brother!"

Suddenly there was a commotion and the whole world shook.

"Show me your face!" "No matter what you do, you’re handsome!" "Ah, I feel like I’m going to collapse……."

But the chaos just didn't seem to end.

The enemies frowned at the shrill screams, and their desperate eyes turned to the one remaining giant.

'He too?'

'It can't be, right?'

'If someone who isn't even a Shaolin monk trained his external skills like that, it couldn't be a prestigious school. It shouldn't be a prestigious school.'

So, the giant took out a papper fan and spoke politely,

"Ah, ahem. Now that I think about it, I fought a life-or-death battle without even revealing my identity. I am Zhuge Lixian of the Zhuge Family."
