\chapter{Chaotic Mess (12)}

The enemies looked very serious at the sudden intrusion of the intruders.

"Look, there is no way to interfere in a life-or-death dispute where two people have a grudge against each other."

"A life-or-death battle based on grudges? Nine men were up against one woman, and you talked about interference? Ha. Really."

"That is what the Heavenly Sword declared-"

"Hmph. That's why I said, bring one more Mid-Peak and fill up the 10-persons team. No, since we'll be fighting together, why don't you bring two Mid-Peak, and three Early-Peak? We can only handle just the right realm, so just bring that much."

"That’s a stretch!"

Then Zhuge Lixian steps forward.

"Stretch? What exactly is stretched? Even if you win nine to one, you'll still be left with our own grudges. In that case, wouldn't it be more beneficial for you if we join the fight now?"

"You said it was a grudge. Is there any reason for more words? I'd rather just have a sword fight."

Peng Daesan added to it.

In Qing's opinion, it was Peng Daesan who always acted cool despite being so disgusted by women clinging to him.

"Ahem. Then we’ll try to get more people—"

For a moment, Tang Lan-ah's eyes light up.

Flash in the shape of a square that crushes the four sides!

"-to match the numbers later, huh?"

The unmanned person who was speaking as a representative looks at the top of his foot in a stinging pain.

The fine needles were protruding with only their heads sticking out.

For a moment, the unmanned person's head turned white.

What the? Didn't that little woman just wave her hand openly? At a time like this?

"An ambush! Such cowardice!"

"Huh! So what of it!? Here, here's the antidote! Now I'm worthy of being your enemy, right? You're not going to fight?"

"Poison, poison!"

Tang Lan-ah's hidden weapons training is a hobby, something she did because she enjoyed it, so it is said that it is better to enjoy something than to master something.

Confucius said, "In a field, one who knows it cannot surpass one who loves it, and one who loves it cannot overcome one who enjoys it."

And the secret technique of the Tang family is not originally thrown one by one.

"What about me?"

"Nine Peak? They're such vile, brainy bastards. If we don't kill them now, they'll chase us around and annoy me for a long time, right?"

When you become the highest ranking member of the Sacheondang family, you don't have to worry about what other people think.

I wish the Tang family would be a little more considerate, but the original villainess doesn't know such things.

If it were an ordinary person, the notoriety I'd accumulated would be a disgrace to myself and my group, in this case, the Sacheondang family, so I would think that I was causing trouble.

The villainess is the opposite.

I think my family and my followers should naturally stand up for me, so what if they complain that I'm a coward?

Are you able to afford the resentment?

"Come on, let’s go! There’s still a lot left."

A child with a knife stuck between his finger joints screams as if he is a fool.

It means that if you step back or try to expel the poison by activating your internal energy, you will be thrown without any regard.

"Damn it! Take the antidote!"

Furious drones rush in.

To be exact, only the seven who were hit by the needle and their connections rushed in with a frown.

The other two? They took a quick look around, slowly backed away, and then quickly darted into the crowd.

Originally, we were planning to fight one with nine, but it ended up being four.

Are you crazy enough to get involved in a fight you're sure to lose?

Were you the one that get poisoned, or am I? You're the one who needs the antidote, not me.

Even in small cities, there is at least one ultra-high-level unmanned officer, and in large cities, there is at least one in every relatively large military base.

That is, the nine came together but did not know each other well, and joined forces to avenge their enemies, but if that didn't work out, they had no choice but to split up.

"Miss, Zhuge, protect Lan-ah!"

"Yep! Sister!"

Qing immediately puts his sword on Nanga Woldo.

The sound of someone pressing their shoulder next to him.

Qing smiles brightly.

Still, two is better than one.

The original specifications of a military sword were a four-foot handle and a three-foot blade.

A miraculous range that sweeps across a huge semicircle of seven feet, a sword with a blade of only two feet long cannot even imitate it.

"Get out of the way! That woman is ambush-"

"No questions asked! No excuses needed!"

"No, it’s not an excuse, you should come first-"

"Die!"

If you keep talking, you'll only damage Lan-ah's reputation.

So, Qing had no choice but to continue to cut off the horse and launch a fierce attack.

The first chapter of the Moon Lady Sword, the first chapter of the Moon Lady Sword.

One day, Wol-ah is startled by the sound of fighting and goes out to see a young man fighting against a group of bandits.

At this time, the young man was badly injured and bleeding, so Wol-ah was startled and quickly stopped the fight.

The world of Wol-ah was only a small mountainside south of Wol-guk called Namrim.

Also, Wol-ah's life is just about playing with monkeys and swinging branches.

So, the grown-up child who still doesn't understand hatred would intervene and say innocent things like, "Why were so many people bullying one person? Everyone has to get along well."

The bandits just giggled at the beauty who suddenly barged in.

At least that was until he was struck by a handsome, straight branch and sent rolling on the ground.

The Unwol-do was constantly flying through the air, light and airy, like a weightless willow branch.

Twenty-five pounds, of course, not quite that heavy, excluding the iron weight attached to the other side, but still, what a sight it would have been to see that immensely heavy lump of iron swinging its length.

This is the first time that Wol-ah has taken up the sword to protect someone other than herself, and it is the first time in her life that she has wielded the sword for someone other than herself.

Huh? is that so?

Suddenly, Qing looks around.

Even though Wolnyeo didn't know it, Qing had already soaked his hands in blood, or rather, not just his hands, but he had jumped in with his nose covered, and had covered up all sorts of blood karma.

The moon girl in the image did not harm the bandits, so she was still innocent and did not know what human hatred was.

But what about Qing?

Was it really necessary to spare the bandits?

Just kill them all and that's it.

The image is shattered, and a crack appears in the line drawn by the Unwoldo.

"Dead!"

The enemy, whose head is broken and bleeding, takes advantage of the gap and extends his sword.

As Qing's grip loosened, the weight shifted to the heavier iron weight at the back, causing the spear shaft to slide down and the blade of the moon sword to tap his index finger.

A shape that looks like a hammer being held in reverse.

As the blue hand advanced and bent its elbow, a heavy iron weight came crashing down from the long spear pole!

A ten-pound iron weight is driven deep into the enemy's cheek.

A chin that rotates, a nosebleed that bursts out in an instant, and a head that didn't explode, even though he seemed to be a top-notch expert.

It bounces back about three times faster than it was jumping in, and crashes down on the other cheek, drawing a long furrow.

The enemies stop, retreat, and turn their heads as they make an emergency landing that scrapes the ground with their faces.

The enemy's appeal flew right up to the audience and wriggled.

And then, bang! A single blade flies and gets stuck between the two plump buttocks of the fallen drone.

The audience's gaze was on Tang Lan-ah.

Tang Lan-ah snorts in amusement and then hides behind Zhuge Lee-hyeon's massive body.

Meanwhile, Peng Daesan is taking charge of the two peaks and is putting up a good fight.

The faint thunder rumbles, rumble rumble, a howl of the air that does not fit under the clear and bright autumn sky.

Honwonbyeokryeokshinkong.

In the beginning, there was no heaven or earth, everything was just mixed together and became chaos.

Therefore, all things were one, one source.

Because it is a huge root, it is called Taewon (太原).

And because everything is mixed up, it is a mess.

One day, when the world was in an unstable state, Peng heard a wall of light coming down with a force that cut the world apart with light.

A ferocious sound of destruction that reaches the body, not the ears. Whatever existed in the beginning must have sounded like that.

Thus, the Tao that resembled a wall appeared in the world, and it is said that the source of the universe, the most fearful sound, followed suit.

Not long after reaching its peak, an unstable river flows over the thin blade of the sword, creating irregular waves.

Even so, he held on to the two and held on with thunderous roar, showing the true power of the Shin Gongjeolhak.

The sword is sharp and its swing is like a flash of light, and it is also sharp and sharp, like a lightning bolt that extends out in countless bends and segments.

However, Peng Daesan was gritting his teeth.

Are you saying that it's not easy to win against two savages of the same level?

If I had known this would happen, I would have taken up the great sword as Sister Ryeo said.

Every day, he would shout, "Yukchamgoldan, Yukchamgoldan," the heaviness of giving flesh and splitting bones, this is the fighting style of a great man, this is the true power of Pangga.

Of course, Sister Ryeo is not a man, but she is more of a beast than a man, so shouldn't she have already killed one and crushed the other?

Come to think of it, wasn't the reason that Pang Dae-san abandoned the great sword and took up the thin sword because of someone who kept shouting about the strongest muscles and preaching the theory of the greatest strength?

Then suddenly I cried!

Peng Cho-ryeo's love for her younger brother was quite extreme. It's fortunate that she can't hug and swing her grown son around now, but how would it have been when she was young?

It means a sister who was always holding her head, neck, and joints together, and conversely, a younger sibling who was always bullied.

Perhaps Peng Daesan's hatred of women began with my sister.

As I exerted my strength without realizing it, the lightning bolt that had been meticulously imitating the lightning suddenly soared greatly, deviated from its orbit, and crashed down in a flash.

A sudden change from easy to medium, the enemy retreats by trampling the ground in a hurry.

Boom! A blade digging deep into the ground.

But there were two enemies, and the one remaining thought this was the moment and drew his sword, and flames shot up from the corners of Peng Daesan's eyes, and he stretched out his hand, and crack!

What's scary about the new skills of a famous family with a long history is precisely this kind of perfection.

Martial arts that were unified with the same image complement each other, eliminate each other's shortcomings, and use them together to create advancement.

Internal energy comes from the Honwonbyeokryeokshinkong.

How to move your legs in Honwonbo.

With your right hand, swing the Honwonbyeokdo backwards, leaving you with one hand left.

So what's in your left hand?

The power of the wall.

The enemy is startled by the force of the wall, so he puts down his sword and defends himself by supporting the blade.

Zzzz! With a sound like breaking rocks, Peng Daesan hesitated and took two steps back.

The opponent was pushed back two furrows behind him, so even though the two retreated a similar distance, it could be said that the enemy, Hosooin, who maintained his stance, won the fight.

Wedge!

The dagger was stuck in the side of the enemy's victim, with only the handle sticking out.

That's why, even in the hometown of Qing, in a fight between many, they say to take down the long-range attacker first.

What if she's a bitch who uses poison?

"Ugh."

The enemy complainant lets out a wet cough.

Paengdaesan rushes at him again, following his example.

The enemy's petitioner thought.

Damn, this life and death situation is really dirty.