\chapter{Chaotic Mess (1)}

As soon as the physician heard that the noble person was injured, she hurried up and saw a rag covered in blood being sewn up on her stomach.

She looked at her and bows her head, saying, "Hello, ma'am."

The physician was startled and took a closer look, but the veins were fine, so she just had to apply some ointment and wrap it well.

It is said that the noble person was originally not prone to getting hurt, so she was sensitive to even the slightest pain, shedding tears and exploding with anger, and the female doctor appeared frozen in place.

But what the heck?

The breathtaking beauty with her bright and gentle eyes looked at her.

She found herself nagging without realizing it.

"No, what on earth is this, Madam? No matter the social status, how can a woman not know how to take care of her own body?"

"Uh."

"First, you should sew it up and rest. Why were you just applying ointment and bandaging it? If it's a scar, you can just erase it with a Jechangsan. Oh my, what kind of scar is this? Why were you torturing your body like this?"

The old woman was startled.

The sight of the back of the Madam, slashed with countless strokes, is so horrific that anyone with weak nerves would faint at the sight.

It was such a detailed piece that it was hard to know where to start, as it seemed to have barely peeled off piece by piece.

"I need to get it sewn up right now!"

"Well, my skin is a bit tough, so it might be a bit difficult to sew."

"How tough can human skin be?"

"Ugh!"

"I applied a lot of anaesthetic, so why is this happening? Urg, no, why is it like this, why won't the needle go in? Urg, grrg!"

"Argggh!"

In the end, she managed to patch up the skin that had not fallen off using a needle used for threading cowhide.

Qing, who's not affected by anesthesia, thought that this time was more difficult and painful than when she was in a life-or-death situation.

Qing slumped down, tears as big as droplets hanging from her large eyes.

The old woman was also exhausted and slumped over, so her heavy breathing was the only noise.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Time flies by for the commander.

Roughly one day is five years.

Well, if the stern mother is cutting down her body in real time, it is only natural that she will age quickly.

\textit{Should I interfere? But Madam has strictly ordered me not to? But am I supposed to just watch this presumptuous act of immorality (the Divine Blood is like a parent) unfold?}

The reason Wang Ssangryong is worried is that a person cannot suddenly change and become a patriotic leader with patriotism.

Even if it's an order, is it okay?

It felt like five cows were grabbing my head and limbs and running off in all directions.

It was Wang Ssangryong who, after watching the duel like that, suddenly acquired the appearance of a veteran, or rather, experience, in just one day.

Even now, I am wandering around in front of the Nosimchosa building, going back and forth, lost and confused, so you can understand the extent of my worry.

Then, knock. Knock. Knock.

The sound of a door opening and closing.

An old, exhausted woman was walking out, looking as if she had lost all her energy.

Wang Ssangryong charges forward like a short-distance horse and mounts his horse.

"What were the details, Ma'am?"

"She’ll be fine if she get some rest."

"Is she okay? She went through such a gruesome battles. Instead of resting, why don’t she take some herbal medicine? Yes, buy some precious jade, or at least some Korean ginseng to protect her body. Oh, don’t worry about gold and silver—"

Then the old woman shakes her head.

"She really just need to get plenty of rest. Martial arts practitioners don't eat or drink recklessly. They're already brimming with energy, so even if you give them herbal medicine, it'll just make them worse. herr skin is damaged, but herr veins were mostly undamaged. All her really need to do is recuperate and rest thoroughly to prevent further complications."

Rather, it was the old woman who had over fifty years of experiences having doubts whether there were such patient in the world.

It was as if someone had meticulously cut through the flesh, leaving the veins intact. Even if they had a deep grudge, it was hard to imagine how a human being could possibly do such a thing. Just the thought of it made her shivered.

Of course, she later found out it was a misunderstanding.

'Hehe, that's not it. It's called a 'Protective Qi', a sophisticated technique that uses Qi to protect the bones and muscles. The skin is a bit damaged, but I have a constitution that rarely leaves scars. This is the true meaning of giving up flesh and taking bone!'

And the young lady had a strange talent for taking a beating, so the doctor unknowingly gave her a harsh slap on the back where she had stitched it up!

Qing rolled on the floor, and wherever the stitched wound made contact, she screamed again, and then she jumped up and stood there dumbfounded, trembling.

The doctor nodded.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Even on the second day of the breast stay, the duel text is raised high without fail.

However, no one came forward and just watched, so on the second day, I just stood there proudly and then came back.

Of course, even avengers have dignity.

After everyone saw the horrific sight yesterday.

Since the blue tail has already wrapped a large piece of cloth around his cheek, wouldn't it be very likely that asking for life or death at a time like this would make him a dirty bastard, regardless of whether he wants revenge or not?

So, someone other than me needs to step forward and prevent the wound from healing.

Anyway, Cheonhwageom's schedule was set.

It is an enemy that surrounds the military on the way to Hangzhou.

There was no need to use the word search, as the city's merchants were already busy preparing to follow the Cheonhwageom's apology march, with idle rascals already busy.

I was worried that he might use his injury as an excuse, but as soon as the noon sun rose, he would raise the flag of resignation.

It means that you will be hated throughout the journey.

So, from the enemies' point of view, there is no need to rush.

So, Yoo Bang-hyeon suddenly becomes the meeting place.

A spectacular scene unfolds where the most advanced warriors search for comrades to take revenge with and practice their combined skills.

Judging from yesterday's performance, it seems like they're an opponent worth fighting if the combination is right.

What about Cheonhwageom's injuries?

Someone will challenge you and hinder your recovery.

However, those 'someones' also thought the same thing.

So no one attacks.

Qing, who was standing there blankly, got tired of it and sat down on a chair.

How could I just sit there and watch you sit alone under the bright autumn sunlight?

The king's twin dragons put up a large sunshade next to him.

We also offer snacks and cold tea as a gift.

Even if it's a miracle, it's not enough to bring all the onlookers and have a fantasy-like eating contest where they wonder if this Jinki Myeonggi is human or a pig.

Slowly, like a bird pecking at a seed, I slowly gnaw on it with the correct eating habits of Ximen Surinryu Miinhaeng.

The onlookers also spread out on the floor and eat snacks, wondering when the fight will end.

The second day ended with me completely losing all tension.

The third day is over.

So, three days of breastfeeding.

After three days, it was time to head to the next city.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The physician was treated with the utmost respect.

Of course, there is no such thing as a free lunch in this world.

Hospitality comes with a price.

Originally, there was a tradition in the Heavenly Demon Cult.

To be exact, there \textit{was}.

For generations, the leader of Medical Division, the first-class doctor of the Heavenly Demon Cult, was called the Demonic Doctor.

But, what kind of person was the Demonic Doctor?

A decent person would not necessarily be fond of titles that contain demons, such as God, life and death, greatness, and sincerity.

So what kind of guy was he?

He was a half-mad former Demonic Adept who enjoyed human experimentation and patient's screams as a hobby.

Since he didn't like the new doctrine of living a good life, he naturally joined the rebel group that was trying to create a 'proper Heavenly Demon Cult' and committed treason.

Those traitors were no longer in this world.

So?

The new religion needs a new physician.

The new Heavenly Demon Cult Medical Division doesn't have time to train its members.

They want a quick turnaround with a moment's notice.

At this time, they met a precious doctor sent by Heavenly Demon. She was also the incarnation of Maitreya Buddha, who sees through the flow of all things.

So, the new believers of the Xuega Sanghoe treated the privates with the same respect as if they were serving their own parents.

So, I was somewhat convinced by the judge's reasoning.

That Cheonhwageom was so pretty that she looked like her own daughter to her elders.

Given such a wonderful environment, I wonder if his nature wasn't so kind.

It was a thought that would make countless dead people shed tears of blood.

The dead don't speak, and whether they shed tears or blood over the subject of corpses, what can I do about it?

It just feels unfair.

The sergeant looks at the man in front of him… … ?

Strangely enough, he was a handsome man, like a woman.

No, to be exact, he is a man more handsome than a woman.

There were thin and slender types of handsome men called midong or miQingnyeon, but isn't this just the appearance of a woman?

It was a very strange sight, no matter how you looked at it, whether it was a man or a woman.

Of course, the man was right.

Why would you just go and play and then go to the bathroom on a trip that you've been on several times?

Then, he saw Xue peeing next to him and confirmed that the snake was a hundred-year-old snake.

Even though he looks like a woman, he is a man among men, a great giant of humanity.

The snake's owner, Xue Ga-nom, casts a fishing line.

"As our company prospers, we were thinking of opening a clinic. Would you be willing to take charge of it?"

"Ahem. I’ve been treated so well, how could I refuse?"

Then Xue Ga-nom smiles brightly.

It was a side effect of wearing women's clothes for a long time.

If you act like a woman, wouldn't countless benefits come flying in just by smiling?

Of course, the judge who saw the snake's true nature was only a little creeped out.

"Sir, what I'm saying is, it's not just a clinic who looks after our society. I want to hang a proper plaque in a large garden and establish a proper school. This includes not only your medical practice, but also self-study."

"Ahem. Now that I think about it, aren’t you more interested in self-study?"

The sage answers curtly.

But already, his ears were perked up and the corners of his mouth were raised, so contrary to his tone of voice, he already has a cold expression on his face.

Well, how could an old doctor not be tempted by the idea of ​​establishing a medical school?

\textit{I was already planning to live the rest of my life leisurely raising disciples, but wouldn't it be better to have several disciples if I were to raise them anyway?}

"Of course, I would like to raise the sign to the name of Sasa Medical School."

The corners of the sage's mouth rise a little more.

\textit{They even said they would put my name for it.}

\textit{Sasa's Medical School! The director's private school!}

\textit{This is the dedication of the director of the Sasa Medical Academy.}

The doctor who read the title in his mind was very attracted to it.

But.

"I'm embarrassed to even mention my name because of my origins. Those Safa guys were just going to watch."

"It's alright. After all, our territory lies north of the Yangtze River. How could those Sapa bastards dare invade? And it's a shame to boast such little number, but don't we have enough warriors in our own territory to hold off the rabble of Sapa bastards?"

"Well, I guess you can tell just by looking at Old Man Choi."

Even the commander-in-chief, Choi Ga-man, wasn't he a master of Unrestrained Realm?

Sasas was a little over ten years older than him, so they just called each other Choi Ga and stayed friends.

"Then, would you please take care of it?"

"Ahem, this old man is shameless. I can’t even pretend to refuse."

"Thank you."

Xuega-nom bows in greeting.

Then suddenly, the old man's intuition, which has been ingrained in him through long life, rings the alarm.

Very ominous, and somewhat deceptive?

what?

Does your sensitivity start to deteriorate after you turn seventy?

The priest tried hard to ignore the ominous feeling slowly rising in his mind.

And then, Xuega-nom continues speaking.

"From now on, I will treat you as the Elder of this company."

"You've been treating me like an elder until now. You've been sufficiently diligent before, so there's no need to be more diligent."

Then, Xue Ga-nom answered with a wicked, extremely evil smile.

"This company has a precious medical book that has been passed down through generations. Would you like to take a look at it?"