\chapter{Chaotic Mess (6)}

Jo Hyeon-ryang is secretly busy.

You might ask, what's the big boss of an honorary position to be busy with, just seeing the faces of precious guests and saying nice things?

When you reach the state of enlightenment, you should start practicing seriously, sit cross-legged for about three days, and meditate while exploring the group.

I would go out even if I only had a few things scheduled for the day.

So, although it may seem to others that he is always playing, he is actually quite busy.

Look at it again today.

Was he the eldest son of the Tang family?

They say a medicine has been developed that can neutralize the poison of Blood Cult.

Why were you reporting that directly to me?

If you just bring me the books, they might come in handy when dealing with the Blood Cult guys later.

But this is how the leader's work is.

As the leader of the Wulin Alliance, if there is a merit or achievement, he should congratulate them in person.

'Well done, great'. 'The future of Wulin is truly bright'. 'A hundred-year-old Dongryang has emerged'.

You may wonder what the meaning is, but these formalities were the bonds of fate that help the political parties unite.

"You were too kind."

The heir of the Tang family bows his head.

The one who came next to him, the youngest and only female member of the Tang family, the precious Geumjeokyeop, the famous Tang family's poisonous flower, also bowed her head.

I wonder why they sent away a child who was always playing around in the family, but I wonder if they were thinking about finding marriage prospect.

That was when.

Wouldn't the Chief of the Escort Force, Ma Jeon-sang, come in and quietly tell the news?

"I apologize for interrupting your visit, but a certain Scholar of Study from the Hannlin Academy is requesting to see you. What will you do?"

He didn't bother to whisper it.

This is not a question to ask the leader, but rather a request for understanding from the guests.

Perhaps the chief of staff, having heard the news, decided that it was necessary to meet him.

Jo Hyun-ryang's expression twitched.

\textit{What the hell is going on? Who am I supposed to meet? The leader's doctor?}

There is no such thing.

The original martial arts leader is sad.

So, while the guests of the party have briefly retreated to the next room, Jo Hyeon-ryang looks at the middle-aged man who has entered the reception room.

\textit{Unrestrained Realm? Isn't he a master?}

\textit{What kind of writing teacher would appear as a master of Unrestrained Realm?}

Of course, when you become a scholar, you were a far cry from the kind of teacher who teaches runny-nosed kids at the neighborhood school.

Isn't he the great teacher of Confucianism?

If you look at it by sect, it would be something like the Daesabom, and if you look at it by alliance, there is no similar position in the alliance, so roughly speaking, it would be something like the acting leader?

Why is such a scholar a master of the Unrestrained Realm?

This made the calculation quite complicated.

No matter how far Yulim has distanced itself from the imperial family, isn't it still the spiritual home of Zhongyuan administration?

The royal family is already suspicious, so I wonder if there is some unknown method of training masters.

There was news that the Embroidered Guard had been causing trouble in Sichuan' Tang Clan before.

It was said that the Embroidered Guard Deputy Commander was a blood demon, a monstrous creature whose body had been strengthened with human blood.

So what did you do in the Wulin Alliance?

What were you going to do?

He just thought, oh, the world is so cruel.

Then should they suddenly put a hood on their head and raise a flag with something written on it like the sky and protest to the royal family?

Otherwise, you can't scold them and admonish them, saying things like, 'How dare the Imperial Palace create something monstrous like that? How can a person do that?'

Or, if the Imperial Palace didn't want this terrible truth to be known, should the Wulin Alliance threaten to give them permission to use gunpowder?

Isn't that impossible?

They knew the shocking and horrifying truth, but so what?

So what?

They just knew that the current government officials were squeezing the blood and sweat out of the people.

It was just that a new awareness of reality was added, that not only was blood being squeezed and applied, but it was also physically applied.

And that monster, created by melting the people, is wreaking havoc on the martial arts world?

So, Jo Hyeon-ryang's mouth becomes dry as he watches the lectures of the Hanrimwon.

Is the government trying to interfere with the martial arts world again?

If a person like Shiganghaksa is a master of Hwagyeong, how many masters were there in the government?

Maybe the Wulin Alliance should rebel against the royal family like those demonic cult bastards.

"Why did Great Man\footnote{巨人;Juren;colossus} want to see me?"

"Please don't call me Great Man. I'm here not as a lecturer at the Hanrim Academy, but as a teacher with students."

"Hmm."

Jo Hyeon-ryang lets out a deep groan.

The meaning contained here was this:

What were you talking about? I have no idea what's going on.

So, is the great teacher who oversees the lectures at the Hanlin Academy, Scholar of Study, a teacher or a disciple?

"Fate is mysterious and elusive. At the end of this net of heaven, a relationship between a master and a disciple was formed. That disciple's name is Ximen Qing."

"Hmm? Were you talking about that kid, Cheonhwageom?"

"Yes. Although I taught her no martial arts, I still took her as a disciple."

Jo Hyeon-ryang blinked his eyes.

"Oh, aren't you mistaken, Giant? The Heavenly Sword already has a disciple and a master. Well, that master, um, can't be like that, right?"

If it were Ximen Surin, who Jo Hyeonryang knew, she would not allow a second master, even more so if it was a man, whether middle-aged or old.

Tian Yuxue smiled brightly at him.

"Dashi knows this as well."

The word 'Dashi'\footnote{大師;'great teacher'} originally refers to a great monk or a great scholar, but it is also used as a term for a second teacher to honor the first teacher.

"Oh. Is that so?"

A smile appears on Jo Hyeon-ryang's face.

What if that crazy bitch admitted it?

After that, I felt relieved and a smile came to my face.

Although the Female Mad Dog is a bit, no, very, no, extremely quirky, she was a true elder of Wulin, a spiritual leader for female warriors, and above all, a dignified warrior.

The reason for exercising her power was to make it widely known that she could engage in negotiations on a deserted island, but in any case, her motives were extremely impure, but she was still a dignified warrior who encouraged good and punished evil.

If Ximen Surin acknowledged him as her second teacher, it also meant that he was not related to any scandalous incidents such as the Demonic Blood Human.

There may be a martial arts tradition that has been passed down in the scholarr's family.

In fact, having one or two household martial arts skills in a noble family is not a particularly unique asset.

Since he was in the government office, he couldn't open a private estate or enjoy business like the famous local families, but it's only natural that a noble family would have at least one or two military achievements.

"So, what’s going on, Giant?"

"Um. Actually, I was just going on a trip to Mount Lao with my disciple."

"Wait a minute, did you say Mount Lao?"

Jo Hyun-ryang's eyes look like they're going to pop out.

Tian Yuxue thought this person was a master who sits second among the top ten masters in the world, and yet he has such a rich expression.

Of course, would Jo Hyeon-ryang really need to hide his surprise?

He was really nervous because he thought it was a government official's business, but as soon as the tension was relieved, Mount Lao came out, so he couldn't help but be even more surprised.

Even without that, there was an unknown rumor going around that there was a Demonic Art secret manual in Mount Lao, so they were gathering a battle group.

However, because the rumors were so blatantly spreading, they haven't set out yet because they reinvestigated and not acting rashly.

It was the difference between the four factions and the four sects.

As soon as the Sapa guys hear that there is a magic absorption technique, they immediately throw everything away and send people to see.

Because I really want to have the suction magic.

However, the Jeongpa must first come up with countermeasures to determine whether the rumors were true, whether there is some kind of conspiracy involved, and what the scale of the situation is and how to minimize the damage to our Jeongpa martial arts family.

The Sapa warriors were so relaxed that they were cursing, saying that since they already had the new martial arts, there was no need to rush.

"Ahem. Sorry for the inconvenience. So, by any chance, about that rumor, that Demonic Art…?"

Tian Yuxue nods his head seriously.

Jo Hyeon-ryang sighed, "Ah."

Tian Yuxue explained the story appropriately.

It was said that Mount Lao was one of the most famous mountains in the world, so they went out to visit it, and heard the evil rumors of the Killer-Among-Killers Demonic Art.

So the disciple became indignant and said:

'Such a terrible evil should not exist in the world, so as a member of the Orthodox faction, shouldn't we track it down and eradicate it from the world?'

"That's right! That's right! It's truly the Divine Dragon! That's the spirit of the Jeongpa, then."

In fact, the adults of the Jeongpa faction already have something stuck in their eyes, so in the afterlife, those cripples who can't even open their eyes and see will be shouting loudly, calling themselves masters, and the wailing will never stop.

Tian Yuxue advised against it, citing the danger.

If that were true, wouldn't the disciple's determination to track down and eliminate the demonic spirit on her own be too strong, and wouldn't it be impossible for him as a teacher to force her to break her resolve?

"That's right. That's right. Being a teacher is truly difficult. If a student insists on taking a difficult path, how can you stop them if the pillar supporting that stubbornness is the council?"

Jo Hyeon-ryang claps his hands in agreement.

As the leader and face of the Wulin Alliance, it is a habit that has grown on me from dealing with people, but this time, I really sympathize with it.

And then I realized that I'm really jealous of Female Mad Dog and Scholar of Study.

This bastard, Hakche, is too busy chasing after women's butts to even discuss matters with Sogaju, but that Cheonhwageom kid is a heavenly righteous man, so he jumps into danger that his teacher can't even bring himself to stop.

What? Did you pick up a good kid?

Or is it time to put into practice the old saying, 'beat them until they become good', which was the Mad Dog's style of education?

'Anyway, so, together with my disciple, I met Murong something and Nan-gong something.'

'Oh, you mean those children? I think they've dispersed and arrived at my house by now.'

'So I went to the tomb of the cursed god, the Shingajimyo, but it turned out that it wasn't a tomb, but a Gu nest erected by the Blood Cult.'

"The Bloody World, that was a very grand name."

"It's exactly the kind of name a Blood Cultist would give you. So, what happened?"

Fortunately, it had been confirmed that there was no such thing as the Essence Absorption Technique.

As she was trying to escape somehow, a woman named Yuanying from Yun family flew in on a coffin and grabbed her, harassed her and forcing her to perform an apology to ask for forgiveness.

The innocent and naive disciple, perhaps embarrassed by having incurred resentment by using someone else's name, agrees to the offer.

Here, even the thick-skinned Tian Yuxue's face turned a little red.

Even though she was a beautiful disciple who I wouldn't mind putting in my eyes, there is a limit to lies. When I think of Qing who ran wild under the guise of being completely anonymous, I say this with my own mouth, but this is a bit much.

However?

"Hmm. If it's that kid, Cheonhwageom, then that's understandable. Ha. She's got a good heart, but how can she navigate this harsh world? And you can't advise her to not do something right, so it's truly a struggle for you, Giant. Tsk tsk."

What is it? Tian Yuxue paused.

Is it right to talk about the same person here now?

Could it be that since there were two XimenQingdo and two Cheonhwageomdo, we were talking about a completely different person than the so-called Wulin Maengju?

Tian Yuxue was in chaos.

What the heck? It's so obvious? What's wrong with that?

Meanwhile, Jo Hyeon-ryang suddenly jumped up.

"Wait! If what you're saying is true, the Cheonhwa Sword is currently being pursued by those vile men who covet magic. Oh my goodness, I need to speak to the battle group right now—no, myself, the commander-in-chief first—"

Tian Yuxue was surprised.

Even if it was the divine dragon of the Jeongpa or something, was it really an urgent matter that would require the martial arts leader to be dispatched immediately?

Looking at the situation, it seems like he's just going to run away with his spear in his hand.

"No! I haven't come to ask for her rescue! Rather, I've come to deliver a message from my disciple, asking the Wulin Alliance to refrain from making any moves, as this could escalate into a major incident!"

"Hmm? Restrain ourself. The future of the martial arts world is being hunted by those vile bastards! How can I restrain myself!? I'm sorry I can't greet the giant, but I'll leave now—"

And then the steps he takes were urgent.

Well, I think Jo Hyeon-ryang is in big trouble, and although Cheonhwageom is Cheonhwageom, if something big happens, then there will be a real storm in the martial arts world.

Would these people, known as the ten greatest martial artists of the martial arts world, simply stay locked in their own domains and leisurely raise disciples?

Since the world can be turned upside down with the flap of a great phoenix's wings, wasn't it a kind of tacit agreement not to move recklessly and cause bloodshed?

So, you should step forward yourself.

It's all well if it was just him intervened as the leader and end things amicably. What if the Mad Dog were to break loose in the world?

That won't do!

At that moment, Tian Yuxue shouted.

"Wait a minute, calm down, sir!"

Jo Hyeon-ryang paused.

"The government? The military?"

"My disciple said the witch had only set a date and time, and that she would use her connections to seek the government's assistance. She said a military escort would accompany her to Hangzhou, so there would be no such situation as Leader fears."

"Ah. That’s good."

Jo Hyeon-ryang breathes a deep sigh of relief.

And then he started crying again.

\textit{Just how deep is that Heavenly Blossom Sword kid's heart!}

\textit{If you're asking me to refrain from doing something so dangerous that it doesn't escalate into something bigger, then you're putting the peace of Wulin above your own safety!}

\textit{As expected, Female Madd Dog's educational policy seems right.}

\textit{I hesitated because he was my precious grandson, but I really have to beat up the young man for the sake of the future of the family.}

Jo Hyeon-ryang calmed down.

This is a conclusion that will only make Cho Hak-che feel wronged.