\chapter{Ximen Qing (4)}

Castigation akin to a bolt of lightning struck down on her.

"What is wrong with your mind?! Is it completely empty? Do you not even know your teacher's surname?! Indeed, it is a two syllable family name. Yes, it may be uncommon. But for you to not know! You make me doubt whether you have common sense!"

"Uh, so the family name wasn't Xi..."

"It is Ximen. Hooo. This foolish girl"

"Ah."

A-Qing felt a bit wronged.

After all, she had seen some people from Zhongyuan have names that were five syllables long.

And she didn't even tell her whether it was Xi or Ximen.

"Qing. My disciple."

"Ah, that sounds...much better."

Qing sounded better than A-Qing.

The name A-Qing was a bit odd anyway.

"That's right. Now that the name is settled, it is time to pass on the important martial arts."

"Oooh, ah."

Qing hurriedly blocked her mouth as her usual speaking habits popped out.

However, it was too little too late.

Thwack! A nuclear noogie flew in.

"With such lacking manners and crude speech...What this old woman is going to teach you is a Cultivation Technique called the Late Blooming Heavenly Love. Since it is also from a Daoist sect, it will not be too difficult to learn."

"Late Blooming Heavenly Love"

"If you reach the Grand Star of the Late Blooming Heavenly Love, there will be no greater achievement for Disciple."

Qing gulped in anticipation.

More than anything, the name sounded cool and it was a martial art being directly passed on by the Zenith Among Women, so it had to be extraordinary.

"What kind of achievement is it?"

Then, Ximen Surin replied.

"You'll become prettier."

"...What?"

"It cultivates beauty."

"Uh...Is that all?"

Bonk! Another nuclear noogie was added.

Qing grabbed her head and made a tearful face.

\textit{I'm pretty sure theres a bump now, isn't there?   }

"The greatest proficiency a woman should achieve in order to conceal herself is by becoming beautiful. Now, I will recite the Sutra to you, so try to memorize it first. '\textit{Sangoyeoil Anmyeongwiji..}'"  

Ximen Surin chanted the Sutra, also known as the formula, of the Late Blooming Heavenly Love.

Qing listened nervously, focusing all of her concentration on the formula.

{\itshape But can I learn martial arts the way other martial artists do?

Well, if it doesn't work, I can just ask them to show me the secret manual or write it down in a book.}

But what do you know?

As soon as she heard the entire mantra, a Status Window Notification popped up.

One new item in the Martial Arts Window.

An Inner Qi Cultivation Technique with a Blue Border had been added.

{\itshape Learning something at the mere Blue-Grade was a bit disappoi-

Euuuk, my head!}

Suddenly, words and phrases uncomfortably burrowed into her head.

"Did you memorize everything?"

"Y-Yes. I memorized it all."

"Memorized it all? After listening to it just once?"

Ximen Surin asked in surprise.

The kid seemed like a completely ignorant fool, but suddenly she could memorize all of that?

"Can you recite it?"

"So like, '\textit{Since ancient times, the most treasured thing has been a bright face that receives love without any action. A talent otherwise known as beauty. There was a daughter among the many children of Yan Emperor Shennong who achieved virtue through this beauty and...}'"

A-Qing recited the phrases that were in her head.

It was just blatant cheating at this point.

However, Ximen Surin nodded in satisfaction, unaware of such wrongdoings.

{\itshape It seems like all of the her talent went into martial arts.

After all, wouldn't that be why a child who should still be crawling has already reached the Late-Stage Peak Realm?}

"Then, I will perform True Qi Daoyin for you. Turn around and sit."

True Qi Daoyin was an act of guiding anothers Qi to directly experience the correct operation of True Qi. 

Half of the remarks regarding how having a teacher was nice was because of this.

After all, even the dullest student wouldn't easily forget what they had directly experienced in their body.

True Qi wandered around inside her body without her controlling it.

It was a fascinating sensation.

A gentle pull went one revolution around the body from the dantian and then returned back to the dantian. 

When it did so, another Status Window Notification popped up.

It was a notification that she had achieved 1 Star in the Late Blooming Heavenly Love.

The Status Window was unpleasant, but she did save some Free Practice Points thanks to it.

"Can you try circulating once? That's right. Well done. You learn quickly. How excellent. You are truly magnificent."

Ximen Surin threw a barrage of compliments.

\textit{As expected, she had the quality to become the next Greatest Under Heaven.}

\textit{Thats right, it was time for a female martial artist to become the Greatest Under Heaven.}

In the first place, martial arts belonged to women.

After all, the method of controlling True Qi originated from the Dark Lady of the Nine Heavens\footnote{Jiutian Xuannu, goddess of war, sex, and longevity in Chinese mythology}, a goddess, because she conveyed the Dao of Nature to people.

When the Dark Lady of the Nine Heavens descended into this world, she concealed her appearance and introduced herself as just an ordinary woman, asking people to call her merely a woman of the State of Yue. The Yue Maiden.

Moreover, the Yue Maiden was also called A-Qing because she enjoyed wearing blue clothes.

And here lies a connection to that very name.

The talent had already pierced through the sky, surpassing the heavens.

If so, she must now be taught the dignity of a female Master.

How should she make this colt-like baby into a proper person?

Meanwhile, Qing was smiling like a fool, dizzy from the explosion of compliments that were akin to a drug.

But if she knew what Ximen Surin was thinking, she most likely would not have smiled like that.

"Then, let's learn methods that care for the head."

"Methods that care for the head?"

"Yes."

"What kind of study is that?"

"It's just as it sounds. It's the method of hair care, which is as vital as life to a woman."

"What?"

Qing blinked her eyes.

\textit{What's with the abrupt entrance of hair care?}

Regardless of Qings bewilderment, Ximen Surin continued.

"I will teach Disciple the forty-two ways of tying hair. You must memorize all of them and be able to do them naturally."

"Um, does tying hair help with martial arts?"

"Oh my. It seems that is all you ever think about."

Ximen Surin took on a stern demeanor.   

"Disciple is already a female Master. However, the worlds view of female martial artists is terribly harsh."

If a female martial artist was weak, they would say, 'What could a frail woman possibly do?'.

Even if she was strong, criticism would follow.

If she lacked beauty, they would say, 'Indeed, if her face is ugly, she should at least be good at martial arts, shouldnt she?'.

If her beauty was exceptional, they would say, 'How many Masters has she enchanted with that face to climb to such a realm?'.

If a male martial artist cut down enemies, making heads fly to the Heavens and blood flow into the Earth, people would praise his firm will and outstanding spirit.

But if a female martial artist did the same, she would be criticized; people would say women committed such violence because they were heartless, terrible, and no different from malevolent snakes.

That wasn't all, though. Even doing righteous deeds to a starving beggar had been met with criticism.

If a man did it, he was praised for his generosity.

If a female martial artist did it, people would say she was just a tender-hearted, weak woman, so she couldn't withstand the harshness of Jianghu.

"Uh."

Qing felt that something was very, very wrong.

"Teacher?"

\textit{I'm a bit at a loss for what to do if you abruptly change paths like that, okay? }

\textit{You're making quite a dangerous statement, you know?}

"Therefore, when Disciple wanders around Jianghu, you must have the mindset of representing all female Masters. To do this, you must always maintain the elegance and beauty of a dignified woman, as well as your own skills."

\textit{I have to...represent all female Masters?}

Qing was horrified.

After all, among all the women in the world, she was the one person who shouldn't ever have such a position.

"Um...Teacher?"

"Now then. Let's start learning, shall we?"

A massive will that allowed no room for rebuttal could be felt.

Qing nodded her head, once again with a tearful face.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

{\itshape I have to get out of here!

ASAP!}

According to Ximen Surin, her personality was like a wild colt, thus impossible to correct.

As such, she said she intended to virtually engrave habits that would make her properly cultivate femininity.

That she just had to stay half a year and then she could descend the mountain.

Thinking half a year might be okay was a grave mistake, though.

Thus began Qing's suffering. 

The core of it was the nuclear noogie.

If even one hair was out of place, nuclear noogie.

If her clothes were not neat, nuclear noogie.

If her footsteps were rough and boisterous, nuclear noogie.

If her manner of speech was casual and crude, nuclear noogie.

If she gobbled up her food instead of eating a meal, nuclear noogie.

If she sat with her legs spread, nuclear noogie. 

It was so bad that it reminded her of a certain dictator who believed nuclear armament was some miracle that could solve national power, livelihood, economy, and even culture.

It wasn't called a nuclear noogie without a reason.

With just one bonk, her lips would shrink back into her mouth in spite of herself.

Her eyes would heat up and shed feel the pain of her skull cracking and scalp tearing.

The only reason why Qing didn't run away sooner was thanks to Chen Changming.

"Sister, are you okay?"

"I feel like I'm going to die. I might actually die if this continues."

"Oh no. What should we do, Sister? You have such terrible hair already, but if this continues-"

Chen Changming gently stroked Qings head.

"Don't pet me. My hairs gonna get messed up."

A-Qing untied her hair and then gathered it back up again.

It was already the twenty-third time today. Two zanzis and one string.

Her hand movements were incredibly natural, even without her consciously thinking of doing it.

Five months. This was the result of getting nuked for five months.

Chen Changming sat down in front of her and presented her back.

"Do mine too."

"It's a bother. Do it yourself."

"I can't be bothered either."

Chen Changming then sprawled out on her back and pressed her head against Qing's stomach.

Qing sighed and asked.

"Which number?"

"Number Thirty-Five."

"Why is it Thirty-Five of all things?"

Qing grabbed Chen Changming's hair.

Hairstyle Number Thirty-Five required her to braid the hair on each side and loop it around.

It was truly tedious to manage. There wasn't a hairstyle that was more of a hassle than this one.  

On another note, in just five months, Chen Changming had transformed from a plain ten-year-old kid into a tiny Female Middle Schooler-chan. 

Honestly, it was more akin to evolution than growth.

Originally, those with rare Innate True Qi like Pure Yin Blood were able to rapidly advance in their Inner Qi Arts as long as their dantian was formed.

Moreover, she had already consumed the effects of the Great Rejuvenation Pill in its entirety.

As such, Chen Changming had already surpassed the Late-Stage First-Rate Realm in terms of her Inner Qi.

As her body became healthier, she grew taller and gained weight.

However, according to Ximen Surin, she had already missed the period for her growth spurt, so she wouldn't get any taller than now.

"It is almost past noon, right? We should go to afternoon training."

"Eung."

Qing then left her dwelling. 