\chapter{Ximen Qing (2)}

"You are finally here."

It was said in a tone that implied she was way later in her arrival than expected.

"You knew I would come here?"

"After all, a woman whose eyes shine with kindness cannot be a cruel evil. As such, your destination must be a place to take the child to. "

The brutal irony of fate had spun around and around in circles until it arrived to hit her where it hurt. Truly, a strange twist of fate.

The innocent, bright eyes that had responded to the pure-hearted strike of the Wudang Sect had ultimately caused her trouble.

A-Qing stepped back with a wary look in her eyes.

As she did so, Yang Caiwu spoke.

"Come. It is already too late to run."

"Lies. I don't believe you. Before, you hid away those black bastards and lied. Theres no one here this time, right? Do you think you can fool me twice just because you fooled me once?"

"I have never fooled you before, though."

Well, that was true.

It was just that A-Qing alone bolted away, thinking this was her opportunity to seize; he had never said something like how he didn't prepare the Net of Heaven and Earth. It was all just in her head.

"So, what. You wanna throw it down here? Settle it once and for all or something?"

"If you hand over the child now, I shall pretend this never happened. You seem like a good person, Young Lady, so there is no need to harm you."

"Ha, I have some skills too, you know? Yeah, let's settle this. You think I can't? I'm also a Master! A Master, I tell you!"

When she said so, the Black Assassin stepped forward.

The sword he drew shone with light.

It was not some mere glow-in-the-dark Sword Qi.

It was a starlight that did not dazzle the eyes but shone in its place, entering ones field of vision with a chilling whisper.

It was Sword Force.

\textit{Uh, what is this. He's a Transcendent Realm Master. To catch just one Peak Realm nobody with a Transcendent seems a bit, well, you know.}

A-Qings indignant tirade shriveled away.

In her days of ignorance, when she had just reached the Peak Realm and feared nothing, she saw a fight of a Transcendent Realm Master in a marketplace.

The blade wrapped in Sword Threads was cut into neat little pieces. Without a single iota of difficulty.

Even though back then he wasn't even her opponent, her knees had wobbled a bit.

This was the dignity of a true Master.

"Sister?"

"Even for me, a Transcendent Realm is a bit...One hit from that and you, me, both of us. We'll be walking on the road to death while split in half."

"It's okay. Even if we go, we'll go together."

"I'm not okay with that, though."

A-Qing let out a deep sigh.

"Excuse me, could you at least give me one sword? Honestly, let's be real here. It's really not fair to make a swordsman fight a Transcendent Realm Master without a sword, you know?"

Neither Yang Caiwu nor the Black Assassin answered. 

Evidently, they didn't want to give even a single sword. 

{\itshape Such cheap fucks.

But seriously, fighting a Transcendent Realm is actually not the move.

I'll just bide my time a bit and look for a chance to dip.

For now, let's try to make them let their guard down.}

A-Qing shouted loudly on purpose.

"Ha. It can't be helped then. Mingming! Ultimate Move!"

A-Qing turned the baby blanket forward.

It was a bit of a struggle because it caught on her chest, but as a result, Changming, who had been behind, now hung in front of A-Qing after a full turn.

A-Qing shouted triumphantly.

"This is the hostage defense technique! You can't attack, but I can! I am invincible and the baby is God!\footnote{'NASDAQ is God'\, a Korean meme}"

After all, they were aiming for Chen Changming anyway.

Furthermore, Chen Changming had a weak body. She could not be so rashly handled. As such, she was the very definition of invincible armor.

It was a truly petty idea and method.

It had been agreed upon in case of an emergency, but Chen Changming still bowed her head in shame and embarrassment.

Yang Caiwu spoke incredulously.

"Are you truly going to resort to such cowardly tactics? Wasn't your goal to save that child, Young Lady?"

"Cowardly my ass! The ones who rush here to shag a tiny kid, causing all sorts of bullshit along the way, are talking about cowardice in front of whom? Me?! The fuck are you on about!"

A-Qing continued to raise her voice vigorously.

"And should our Esteemed Little Baby just watch other's affairs as if it's none of her business? Do you think she's going to leave her life in the hands of someone else and just shout, 'Let's go team! Win!'?! At that point, why not just outright ask someone else to live her life for her?! Don't you dare underestimate our Changmingie, you punk!"

Then, an unexpected response came back.

"Your words are truly admirable!"

A woman approached, clapping her hands.

She was a middle-aged woman who just had to be called beautiful. There was no other way to describe her.

Despite the traces of time, her face was alluring, as well as dignified.

"Last night, the constellations appeared quite ominous, so I went for a walk. But before I knew it, I was outside the mountain gates. I intended to overlook the affairs of the secular world, but then, the child spoke such lovely words. Child, what is your name?"

"Me?"

"Yes, Honey."

"I'm called A-Qing."

"A-Qing! What a lovely name. But what in the world is this appearance? Not even a piglet would carry itself like this. And your sister too. How can you sisters be in such a barbaric state? Tell me. Are you a person or a piglet?"

It was a lady with a peculiar dignity.

To the extent that it made A-Qing think, perhaps a chaebol's wife would carry herself like this.

"I'm a person."

A-Qing answered, her voice shrinking back.

"Then, act like one. Moreover, what is this state you're in? How could you treat your own body like this? You should know how precious it is. You are practically pieces of rags, aren't you?"

"Um, excuse me, Madam, thank you for your words and all, but its a bit dangerous here, so it would be better if you stayed away That bastard with a sword and that bastard with a spear are really bad people."

"Are you seriously in a state to worry about me? While looking like that? I think it's more right that I'm supposed to worry about an idiotic bitch like you. You can't even take care of yourself, you halfwit. Haaaa, this is so infuriating. My chest is all stuffy. Haiya."

"Uh..."

{\itshape What the hell is going on?

Why am I the one being scolded?}

A-Qings eyes shook with bewilderment.

While she was doing so, the Madam turned towards the other two men.

"And you, if there was even a little, just a tiny bit of sense in your heads, you wouldn't dare threaten a woman in front of Mount Wu's gates. Do I really have to rebuke you for having an intelligence that is worse than a bug's?"

The faces of the two men went utterly pale.

Though A-Qing was unaware, it was because the lady's sheer presence had already made them feel sick to their stomachs.

They had immediately recognized the lady's identity.

When asked who the strongest martial artist was, one could argue for ten straight nights over the answer. In fact, it was a common debate in Zhongyuan, happening anywhere at any time.

But if asked who the strongest woman was, there was only one answer.

The Zenith Among Women, Godmother Ximen Surin.

Yang Caiwu made a fist palm salute with a pale face, utterly void of blood.

"Elder Godmother, I was-"

"Stop. You know who I am. If you do not believe your excuse to be honorable, it is better to keep your mouth shut."

Yang Caiwu shut his mouth.

Desperate as he was, there was no reason to choose suicide just because of desperation.

The moment he started talking about Pure Yin Blood in front of the Godmother, his life would be forfeit.

It was common sense. Very, very much so.

"Haiya, just get lost. I can't stand to even look at you."

And with those words, A-Qing received a notification, signaling a Mission Completion.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was an unfamiliar ceiling.

A gentle fragrance comfortably filled her every breath.

A-Qing sat up.

She was inside a neatly-arranged room.

As soon as she arrived in the Divine Maiden Sect after following the Madam, women with expressions like they'd seen the most terrible thing in the world rushed in and plunged A-Qing into a bathing tub.

That was when A-Qing realized why cats so desperately resisted baths.

If left alone, she would somehow manage to keep herself clean.

But if she was suddenly dunked in water and scrubbed with soap, of course, she was bound to be startled.

Moreover, she was manhandled and violated by numerous hands of women she had never even met before, much less known their names.

All A-Qing could do was tightly close her eyes and pray for this time to quickly pass.

Afterward, she was treated by a female physician.

She kept getting smeared by something and was patched up in so many places that she hardly needed to wear clothes.

Then, she had a bit of warm broth and fell asleep.

And now, she had woken up.

Now that she actually looked like a human being again, a warm fatigue pressed down on her entire body.

A-Qing staggered out of the room.

And there, she saw Ximen Surin drinking tea on the wooden floor.

{\itshape That Madam was called the Zenith Among Women, right?

The strongest female in Zhongyuan, they say?

Just as I thought, people had to become Masters. 

She didn't even draw her sword. She just swaggered over and stood there like a boss, before saying

'Get lost.'

With just that one word, those bastards fled in panic.}

"Child. Have you awakened?"

"Yes. Thanks to you. Thank you."

A-Qing sneakily glanced at her, trying to gauge the situation.

Let's test the waters, huh. Taste Test Ability! Begin!

"I've heard the whole story from the little baby. Well done, well done. Truly commendable. How could you take such lovely actions?"

"It's nothing. It was something I obviously had to do, after all."

"That very thing which should obviously be done is not carried out by many. As such, how can I not praise you?"

Ximen Surin laughed heartily and continued.    

"At any rate, I have truly experienced something startling. How is it that a child born with Heavenly Slaughter grew up so upright?"

"Uh..."

"How did I know, you ask? Didn't I already say that last night's constellations seemed ominous? A dreadful and treacherous star seemed to flash before my eyes. How could I just stand by? I had to look around."

"Can you tell that just by looking at the stars?"

"How could I know that just by looking at the stars? Here, give me your hand for a moment, why don't you? Let me feel your pulse."

A-Qing obediently extended her hand.

Right as she did so, Slap!

Ximen Surin's fingers struck A-Qing's wrist.

\textit{No, wait, what the fuck? Why does a finger slap hurt so much?}

A-Qing almost shed tears, as she clutched her wrist in pain.

Ximen Surin clicked her tongue.

"Tsk tsk. Foolish child. How can a martial artist so readily offer their pulse? How did I know, you asked? While I knew it was close because I saw the stars, feeling your pulse was what actually revealed the presence of the Killing Star within."

"You can tell that by feeling a pulse?"

{\itshape What the hell?

Is she a Master while also being some great figure of herbal medicine as a side job?}

"At my realm, you come to know these things."

{\itshape Just as expected, one just had to become a Master!

If you become a Master, you'll know how to do anything and everything!}

"So be more careful. I can see that your nature is upright and just, so I shall overlook it, but others, knowing you were born with Heavenly Slaughter, will not hesitate to attack you without reason."

"Ah."

This truly was a useful piece of information.

After all, she could have been abruptly attacked without even knowing why.

\textit{Remember not to offer your pulse carelessly. Important. Star that shit. Stamp.}

"Indeed. Perchance, do you have any thoughts of joining the Divine Maiden Sect? "

"Thank you for such a kind offer, but I don't plan on joining anywhere just yet."

"Well. I thought as much. Heavenly Slaughtering Star. Born of Heavenly Slaughter from the front and destined to live as a wanderer from the back, you are trapped in between these two inescapable fates. You are clearly not meant to settle in one place and set down your roots."

It wasn't such a grand and excessive decision, though.

She just picked it based on a guide she read.

How could she have possibly known she would get killed if she was ever caught harboring such a destiny?

Despite the harsh words, A-Qing remained utterly unbothered, listening as if it was someone else's problem.

The Zenith Among Women asked again with a gentle smile.

"Then, do you have any thoughts of becoming my disciple?"