\chapter{Ximen Qing (1)}

A-Qing emerged from the cave.

The weather cleared and the sky was entirely crimson due to the sunset.

Having entered in the evening, she had basically stayed up all night.

If it was up to her, she would have spent as long as possible before escaping, but she was hungry and thirsty, so staying any longer would likely deplete her strength and put her in even more danger.

Besides, Chen Changming, being physically weaker than her, couldn't endure like A-Qing.

Despite being exhausted, sore, and in pain everywhere, now was the perfect time to attempt a getaway when her dantian was filled to the brim.

Since the sun would set in the west, north was that way.

She ran straight north, then somewhat westward, thinking that if she saw some huge mountain along the way, it would probably be Mount Wu.

However, A-Qing underestimated the mountains of the Zhong Yuan.

To a cultured and civilized modern Korean, a mountain implied a large hill with rounded ridges and soft peaks.

But in the Zhong Yuan, mountains were insurmountable obstacles that humans would not dare to traverse.

Moreover, Mount Wu was part of a long river flanked by cliffs, originally known as the Wu Gorge.

For this reason, something resembling a barrier appeared as an obstacle that partially blocked the view between the forest and the plains.

{\itshape What the hell is that. Is that what a mountain range is?

Which one among all that is Mount Wu?

Then how am I supposed to find the Divine Maiden Sect?

Do I have to rummage through the entire mountain range or something?}

For a moment, her vision went dark at the thoughts of going through such tedious suffering.

"Hey, do you know which one Mount Wu is from there?"

"Dunno."

"Of course you don't. What did I even expect. Then do we have to go over there?"

At the foot of the mountain, there were clusters of black-roofed houses.

It was a type of village commonly seen in Zhongyuan.

"Ah shit, those kinds of neighborhoods always have shitty people, though."

The remote villages of Zhongyuan were not gatherings of people living a quiet, pastoral life, completely unchanging day by day. 

The villages structure already proved that.

Positioned on a mountainside, the houses below served as a wall, while the top had a watchtower and a command post; basically, it served no differently from a small castle.

It was a long-standing tradition in Zhongyuan to kidnap people from neighboring villages if there was a shortage of manpower.

Women were matched with single men and men were made into slaves. Depending on the relationship with that particular village, the treatment of slaves varied widely, from being treated as a close subordinate to being used as an outlet to vent their frustrations.

However, neighboring villages and cities would laugh it off, saying that was something from the past and who even lived like that anymore.

However, some remote neighborhoods did indeed still live like that.

It was a shocking reality she had witnessed during her travels.

A-Qing slowly approached the front of the village.

As there was a large door connecting the gaps between the houses, it was essentially a city gate.

The young man sitting atop it, perhaps acting as some sort of militia, abruptly jumped up.

"Oh my, oh my. Whats this? Is it a ghost or a person, ya?"

"I'm a person."

"Would a ghost say they're a ghost, ya?!"

"Then what do they call themselves?"

"About that, ya...Pah. What tricks are you playing, hah?!"

A-Qing sighed deeply.

"Forget it. Are there any outsiders inside? "

"Outsiders? There's none, ya. Who would come to such a place, yanno?"

A-Qing was somewhat relieved by this.

It seemed the black-clad bastards hadnt reached all the way here.

"Then, since I'm here, can't you let me in?"

"With that appearance, ya? Not a chance, Ghost Girl."

"Agh damn. Then can you at least tell me where Mount Wu is?"

"Mount Wu, ya? Why you looking for such a far away place, eh? If you go that way for a bit, the highest peak you see is that Divine Maiden Peak, yaya. All of that is Mount Wu, ay,"

"Ooooh. Divine Maiden Peak."

Divine Maiden Sect. Divine Maiden Peak. It fit perfectly.

"But can't we rest here for just one day?"

"Oho. Ehhh? Yaya, no no."

"Or at least give a few cold dumplings. The kid is really hungry."

"Ehhhh? Goodness gracious, hah....Are you carrying a baby on your back, ya? You weren't some hunchback?"

It was the very first impression of a K-Baby Blanket for a person of Zhongyuan.

The militiaman muttered, but was easily overheard by a Master. 

-Ive neva heard about a ghost with a kid, ya

\textit{Hold on, stop right there. Why does he keep calling me a ghost when I'm perfectly alive?}

A-Qing gritted her teeth, unaware of her own appearance.

After rolling in the mud and being caught in the rain, her appearance was far from human by the standards of Zhongyuan.

Yet, by some stroke of luck, her appearance garnered sympathy.

It was because the people of Zhongyuan were more generous to ghosts than to humans.

There might not be food for a beggar, but there was always meat for offerings to place in front of a Buddha statue.

And they said things like how people could be driven away, but on the off-chance that some vengeful ghost clung onto them, it could haunt their family for generations. Or something like that.

"Stay right there! I'll bring something right away, yah."

"If there's warm soup, that would be great. It was cold all night."

"So many demands, ya!"

"Ah, also some alcohol."

"I'll ask around, ye!"

After the militiaman disappeared into the village, A-Qing released Chen Changming and flopped down right then and there.

Chen Changming snuggled into A-Qings embrace, settling herself within as if it was only natural for her to do so.

"What's with you. You're heavy."

"I'm cold."

"Tch. What are you even going to do with such a frail body?"

A-Qing hugged Chen Changming and rested her chin on her head.

"It would be nice if they give something tasty."

"I'm hungry."

"Me too."

At first, it wasn't all that important, but as soon as they thought of how food was coming, their hunger suddenly erupted, consuming them inside-out.

-Grams, it's a ghost! A ghost, I say, ya! A ghost with a baby, at that!

-A ghost, meh? Let's see, ye? If it's some trivial ghost, just let it go on its way.

A-Qings ears perked up.

If it's a trivial ghost, let it go on its way.

And if it's not?

A-Qing infused her hands with True Qi.

A faint bluish glow with deep blue threads rippled around her hands.

Come to think of it, even though she was a swordsman, being called a Daoist, Fist Practitioner, Palm Expert, or whatever didn't sound all that great to her. 

Glowing with ones own True Qi indicated a realm that had reached Transcedent Realm.

The likeness made by a mere Peak Realm like her was nothing more than glow-in-the-dark stars one would stick on a childs bedroom ceiling.

-Oh my, that's no ordinary ghost, ya.

-Grams, the dishes, ye!

-Prepare a hearty meal. If it sticks to us, we'll get haunted for the rest of our lives, ya. Watch over those kids especially, hyuh. Gazing too long at it might bewitch them. Wouldn't want an absolute disaster at home, ye?

\textit{Wow, this actually works, huh.}

A-Qing smiled contentedly.

And the result was quite satisfying as well.

She wasn't sure whether the chopsticks stuck in the rice bow were intended to hasten their attainment of Buddhahood, though. 

Rice was piled high with pickled vegetables.

And more pickled vegetables were served alongside pickled vegetables.

Furthermore, a soup, made with all kinds of fish, was just the thing for a cold, empty stomach.

After becoming somewhat full, A-Qing sipped the cloudy alcohol that was served.

A-Qing knew absolutely nothing about moderate drinking. In fact, she didn't give a fuck.

After all, food was food and alcohol was alcohol. There were separate stomachs for those things.

Apparently, because they thought a child ghost was present, they brought out a few baked sweets; Chen Changming nibbled on them inside A-Qing's embrace while gazing up at her.

However, rather than the cup of alcohol that was continuously bobbing up and down, something else caught Chen Changming's eye.    

"Is your...hand okay?"

"It's not that it's not, not okay."

The two dangling fingers were somehow fixed back into place. They were swollen and stiff, unable to be moved.

After thinking for a long while, Chen Changming spoke.

"So, it's not okay."

"Correct. It hurts like hell. But since everything hurts all at once, I'm not all that bothered by it, you know?"

There was a hole in her thigh and the stitched wound on her forearm had reopened, thus bleeding again. Mud mixed into the scrapes made her entire body sting and itch; a absolute fucking shitfest.

There wasn't a single joint that wasn't sore and dirt crumbled and crunched in her hair.

However, being in such a mess actually felt rather comforting.

It was like the easygoing nature of middle-aged reserve soldiers.

It was a similar principle to how wearing a military uniform practically turned the sky into a blanket and the earth into a bed.

Feeling full, thus sprawling out for a bit, it had soon become dark around them.

A-Qing wrapped Chen Changming up and put her on her back again.

It would take two days if a villager walked, but A-Qing could make it in half a day by running.

If she went a bit slower, it seemed about right to arrive by dawn.

Then, all she needed to do was head to the highest peak.

"We'll probably arrive at dawn. Little Baby should sleep. It's said that people need to sleep well to become a beauty, so it seems like Little Baby needs to sleep all day."

"What are you saying. Um, then, then, if that's the case, Sister \footnote{Unnie in the original text} has to literally hibernate, you know?"

A-Qing flinched for a moment.

It was an unfamiliar form of address.

She could feel Chen Changming fidgeting against her back.

Even if she was a martial artist, she wasn't capable of turning her neck 180 degrees, so she couldn't see her expression. But-

It was almost like a question.

As if asking if it was okay to call her that.

Sister might be a bit odd for a man. But to be fair, men of modern times also used the term Sister when amongst themselves.

A-Qing let out a brief burst of laughter.

"Well, why not. We're fated to be together until we reach the Divine Maiden Sect anyway."

Arriving there wouldn't magically cure Female Middle Schooler-chan and turn her into a healthy companion or anything like that. There wouldn't be such miracles.

After dropping her off, who knew when they would see each other again, right?

"Go to sleep quickly. Don't drool all over my back, though."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The pitch-black sky gradually turned azure.

The sound of chirping birds.

Even though the sun was still below the horizon, its presence empathetically announced the dawn.

She had worried about overshooting their destination throughout the night.

But upon seeing the Divine Maiden Peak, she realized it was an unfounded concern. With its towering presence, standing there all in its lonesome, there was no shot she could miss it.\footnote{The actual Divine Maiden Peak look very distinguished among the Mount Wu scenery}

\textit{But honestly. Be for fucking real. How am I supposed to go up that?}

Rather than Divine Maiden Peak, it was just the Divine Maiden Tower.

It was as if a tower had risen one more time from the mountain top.

In the first place, not even half of a half of the mountain was covered with greenery.

The rest was composed of vertically extending gray bedrock. 

Still, if humans lived here, there should be some kind of path to climb up. As such, she was currently wandering around, trying to look for a trail that would make it easier to ascend the mountain.

Upon reaching the very corner at the end of the mountains base, a depressed terrain between two ridges appeared.

And at that place was a road, hardened and killed by the continuous stomps of people and carts.

Also, at the end of that path stood two people.

That Xinchang thingamajig? Isn't that Whatchamacallit Clans. Someone.

She couldn't quite remember the name, so...

Also, there was one oh so loathsome ninja as well.

At the same time A-Qing saw them, they saw A-Qing as well.

\textit{If you blah blah into an abyss, the abyss will blah blah into you or something.}

A-Qing recalled Nietzsche's famous words that were known to anyone and everyone.
