\chapter{Ximen Qing (5)}

Qing lived separately.

Qing was the direct disciple of Ximen Surin.

However, that did not make her a disciple of the Divine Maiden Sect.

Because of her unusual position as a disciple of the Grand Elder, yet external from the sect itself, she could not enter Flower Pond Hall, where other sect disciples lived.

It was because she was considered too great a senior.

Ximen Surin, a Master who had even achieved Body Reconstruction, was a figure from the previous generation. 

As she had already passed on the position of Sect Leader to the most senior disciple, Qings allocation was that of the most Junior Sister of the Sect Leader.

However, there was a culture among the Daoist Sects that stated, 'It's not like we are strangers!'.

As such, Daoists roughly shared and respected the allocations of each others sects.

But one thing must be kept in mind; excluding Shaolin and Emei, the Nine Sects, renowned throughout the entire world, was no different from one big Daoist Sect.

And the influence of the Nine Sects was equivalent to that of the entire Orthodox Faction of Wulin.

Therefore, this allocation was essentially an authority recognized by all sects classified as Orthodox.

Initially, Qing did not know about this strange system of allocation.

However, she discovered that it was some kind of a standard or rank.

It was similar to a certain standard that was obsessively adhered to by a specific military branch with the goal of coming back to land. 

Order of entry determined the rank which they were assigned, not much different from the modern military, but sometimes there were exceptions.

It was because of the oh-so-great Masters who picked out talented newcomers, thinking, 'This one will be strong if raised well'.

And once becoming the direct disciple, the disciple was included under the Master's standard, or in simpler terms, under their banner.

For this reason, Qing was equal to the highest seniors in the Divine Maiden Sect, excluding Ximen Surin!

So it became like this.

"Ah, it's Great Junior Grandmaster"

"Great Junior Grandmaster! Hello!"

"Great Junior Grandmaster! Did you have a good lunch!"

Ah! A wild disciple(s) of the Divine Maiden Sect appears!

Qing was surrounded by a group of Divine Maiden Sect disciples.

Ximen Surin had firmly declared to the sect disciples that she would be the next Greatest Under Heaven.

It was the minimal justification needed for the sects administration to accept her as a direct disciple considering the allocation issue.

But far from being arrogant or annoying, Qing had a talent for acting respectively and friendly towards elders.

And it was the same for the lower-ranking sect disciples as well.

Qing was not a difficult character to approach, and strictly speaking, since she was an external figure, there was no need for stiff formalities.

As they had grown up within the sect and maintained a girlish carelessness, the young female sect disciples became curious about the outside world, causing a fuss every time she indulged them by telling them stories. 

For this reason, Qing was insanely popular.

"She's busy. Move aside."

At that moment, Chen Changming blocked the way as if to protect Qing.

"Little Junior Master was here."

"Agh, our plans are ruined."

"We'll get going now, Great Junior Grandmaster!"

"We'll see you soon too, Little Junior Master!"

The sect disciples left with a disappointed look.

Qing was easy to approach.

They instinctively knew that, for some strange reason, Qing found them intimidating. 

But it was different when Little Junior Master was by her side.

Normally, Little Junior Master was gentle, quiet, and cute.

But they were well aware that she growled like a beast, as if marking her territory, when next to Great Junior Grandmaster.

Of course, Chen Changming was doing well too.

Qing had seen several times a day how the disciples of the Divine Maiden Sect carried the small and petite youngest Junior Master like a doll.

It was understandable.

The tiny thing always waddled around with a sulky and pouty expression.

She was indeed pretty cute.

Qing always just watched, not daring to touch without the Female Middle Schooler-chan's permission.

"Then, work hard today too, little kid."

"Sister too."

Qing parted ways with Chen Changming in front of the Divine Plum Temple.

And then she headed towards Ximen Surins Temple of Water and Moon.

The gates to the Temple of Water and Moon were always wide open.

But hardly any sect disciple dared to enter.

After all, it was difficult to enter the private dwelling of the Grand Elder on their own and within the Divine Maiden Sect, Ximen Surin was known to be fiercely scary.

However, Qing found this a bit pitiful.

It was obvious why the gate was left wide open.

It meant anyone was welcome to enter.

But with the Divine Maiden Sect disciples freezing up like mice in front of a snake at the sight of Ximen Surin, who would dare to find the courage to visit?

But that didn't mean the sect disciples were to blame.

In modern terms, it would be like barging into the chairman's office because the chairman seemed lonely.

Perhaps the only person capable of such an act would be a director from an external company who suddenly parachuted in without any basis nor reason.

And that very external director boldly entered the Temple of Water and Moon without any basis.

"Teacher, Im hereeeee."

"Ha. How can a dignified martial artist snort and act all coquettishly. Are you trying to act cute? My disciple, always remember to behave with the dignity befitting a representative of all female martial artists and-"

"This child doesn't know about that stuff. This child only knows martial arts. Please teach me martial arts. I'm getting dizzy from the withdrawal."

"Ehhh.. You're not even pretending to listen anymore."

Ximen Surin voiced her displeasure, but she couldn't completely hide a faint smile.

Qing clenched her fist tightly.

Whenever she succeeded in acting all cute, the severity of the nuclear noogie tended to decrease to that of a tactical nuclear noogie.

The studies with Ximen Surin now continued only through sparring.

Qing acutely felt the truth that the more Inner Qi one had, the better. As such, she had swiftly advanced through the Late Blooming Heavenly Love Cultivation Technique, reaching the 10 Star Realm in no time. 

Naturally, Ximen Surin was amazed to see the child, who had been walking until yesterday, suddenly flying around.

At that moment, Ximen Surin was contemplating whether to pass on the sects Divine Arts. Sure, she was her disciple, albeit peculiar, but since she was not a part of the sect, it was somewhat embarrassing to push for her to be able to learn it.

Indeed, the cultivation technique given was not that difficult to learn. However, the fact that she achieved the Grand Star of it in just one night was enough to convince her. She thought, 'As expected, she will be the next Greatest Under Heaven', and decided to transmit to her the Cultivation Technique of the Zenith Among Women.

Zhu Xiangs Heart Cleanse Mirror.

It was a Divine Art said to have been created by Yan Emperor Shennong for his daughter, Yaoji.

Qing joyfully poured her Practice Point into this Purple Border martial arts.

That night, a phoenix\footnote{Fenghuang} soared from Qing's dwelling.

Zhu Xiangs Heart Cleanse Mirror 12 Star. Grand Star.

Qing's Inner Qi swelled by a terrifying amount.

But that was all it did.

Ximen Surin began to worry.

The amount of Inner Qi was enormous.

Despite the insufficient size of her dantian, the Inner Qi inexplicably remained throughout her body and limbs.

By the amount of Inner Qi alone, she was already on par with a Mid-Stage Transcendent Realm.

But why couldn't she break through the wall of the Transcendent Realm?

Thankfully, it seemed like a Master was not a Master for no reason.

Ximen Surin eventually found out the reason.

"I see. All movements and techniques come from Disciples head."

"Then where else should they come from?"

"They should naturally arise from the heart. My goodness, it seems being too smart has its drawbacks. That is why youre in this state. Too much is as bad as too little, after all."

High-level martial arts were inherently vague.

For example, in swordsmanship, one might write about lifting the sword and striking it down quickly like this.

\begin{quotation}
\textit{	When striking down swiftly from a mountain high in the sky to a hill, its momentum akin to a storm..}
\end{quotation}

It was like this.

The issue was not just the operation and form of martial arts, but the Imagery must also blend together.

Usually, a martial artist would enter a Trance and achieve the Peak Realm when they fully understood the meaning behind such phrases.

To expand on that, the act of completing ones own interpretation was the very definition of Imagery.

Fully integrating even a single movement as ones own technique was what allowed a martial artist to enter a Trance and reach the Transcendent Realm.

"Imagery..."

"Since you only understand Sword Arts with your head, it is only natural that you cannot reach the next realm."

Of course, that was to be expected.

Qing's method of learning martial arts was just to forcibly cram them into her head.

"So what should I do?"

"Well, you have no choice but to swing your sword until such Imagery arises and establishes itself in you. Isn't that so? "

As such, it was sparring, more sparring, and yet even more sparring. Never-ending spars.

Honestly, it was an extremely difficult task.

That's because-

Thwack!

"Hasn't your hair become a mess? Hurry and fix it. You are like an unkempt brat of a disciple."

Thwack!

"There were six paths of living, yet you couldn't find any of them and ended up rolling on the ground? I have repeatedly said that it is imperative for a female Master to be graceful."

Thwack!

"Can you not see your front opening? Men and women are distinct! How can you expose your undergarments in a mere fight?!"

Qing clutched her head, making a tearful face.

"Ack. At this rate, your disciple's head will break."

"What break? Anyway, why in the world is it that that wild temperament of yours can't be fixed..."

When Qing floundered around, making a fuss over how she would die from the agony, Ximen Surin would sometimes soothe her with a somewhat softened attitude, stroking her head.

Ximen Surin looked at Qing, moving her hand.

When she first came to the Divine Maiden Sect, her appearance was not bad but not particularly good either.

The Late Blooming Heavenly Love Cultivation Technique was excellent when it came to a womans cosmetic treatment.

The Zhu Xiangs Heart Cleanse Mirror, the Divine Maiden Sword Sutra, and the Divine Maiden Footwork were also the Fairy Arts of Daoism, thus the more one got accustomed to them, the more their beauty was enhanced.

As a result, her features gradually found their place, eventually reaching the present state.

Now, she had reached a point where she would be called a beauty no matter where she went.

Almost no one would remember the unsightly brat from before.

\textit{At this point, I don't need to hold her back any longer.}

Ximen Surin made up her mind.

"It is about time for you to go out into the world."

"Eh? Really?"

"Holding you back any further will not bring you to the Transcendent Realm. What you need isn't this mock duel but an actual battle. I have taught you all there is to teach, so staying any longer will not mean much."

"Ah..."

Qing had seen the Omen Mission before.

If there was an Omen Mission, it inevitably meant that a Main Mission would follow.

As such, Qing had to verify it.

Life in the Divine Maiden Sect was satisfying.

But she could not just sit by idly, continuing to laugh and chat while remaining ignorant.

She had to confront this Status Window somehow. She had to come to a conclusion once and for all. 

Only by seeing the end of this game could the ensuing emptiness turn Qing into a complete person.

Whether that meant returning to reality or remaining a person of Zhongyuan forever.

"Even though Disciple was not a part of the sect, none of the sect disciples here think of you as an outsider."

"I know that too."

"I see. It is a relief that you know."

Ximen Surin stroked Qing's head as she spoke.

"Your thatch will still be here, so come back and rest whenever you like, Disciple."

"Uh...Can I do that?"

"Of course. Is that even a question?"

Ximen Surin smiled benevolently.

It was a smile akin to one given by a mother.

"This is your home. Who in the world would ever need permission to come and go when it is their own home?"