\chapter{Ximen Qing (3)}

A-Qings eyes widened.

Even with her lacking common sense and limited knowledge, A-Qing knew that to learn martial arts, one must become a disciple, and to become a disciple, one must join a sect.

No, to be honest, she didn't know at first.

But she found out while looking to learn various martial arts in the early stages of her journey.

"I don't need to join the Divine Maiden Sect?"

"Let me be honest with you. The talent of a child not yet twenty who has reached the Late-Stage Peak Realm is very desirable. There wouldn't be a teacher in Jianghu who wouldn't want you."

A-Qing was surprised.

"Am I that young?"

"Child?"

"My figure isn't exactly girlish, though."

And her face was already the lowest score possible in terms of looks.

"Child. Perchance. Do you not know your age?"

"Probably."

"And the name A-Qing was also made by you?"

"Yes."

To be more precise it was Ctrl+C, V. She copied and pasted it.

After all, the post said only then would she be given Purple Martial Arts.

"What is your original surname?"

"I don't know that either..."

Ximen Surin's expression turned into one of pity.

It was the same misunderstanding as a certain someone from Hebei.

"Oh my, you poor child. How did you grow up so well in such hardship? How admirable. You are truly lovely."

A-Qing just awkwardly laughed off her words because she didn't know how to reply.

"I see. But still, you did seem to have some luck finding a teacher."

"A teacher?"

"...You don't have a teacher either? Then where did you learn your martial arts?"

"I just happened to get to know it..."

"Self-taught?"

"I guess?"

A-Qing replied in the form of a question.

After all, it wasn't a martial art learned through a proper nor standard method.

Ximen Surin's expression turned to one of shock.

"The pure and profluent flow was clearly the meridians of orthodox Daoism. And wasn't it clearly a cultivation technique that is not lacking to be called a Divine Art? What an exceptionally curious coincidence. What is the name of that Qinggong? That cultivation technique? "

"The Yue Maiden Cultivation Technique."

Ximen Surin slapped her knee.

"Oho! So that is why you are A-Qing. How truly amazing! I thought such a Divine Art only existed in legends, yet here it's master is, right before my very eyes. Indeed, the Heaven and Earth of Jianghu is vast and there is so much humans do not know! But-"

Bonk! A noogie flew towards A-Qings head.

Escape? There was no escape. The bonk came at the speed of light.

An impact so shocking that it shook her skull.

It was practically a nuclear noogie, shot from an ICBM.

A-Qings eyes instantly welled up with tears as Ximen Surin spoke sternly.

"How can you answer every question so readily? You foolish and lacking and naive girl. If people knew of your martial arts, the entire world would chase after you out of greed, Child. You are lucky to have survived until now. Tsk tsk. "

"Oooh."

She gained yet another piece of precious knowledge.

The Madam was like a common sense vending machine.

Every time she tapped it a bit, important knowledge and wisdom just cascaded out.

"'Oooh'? What a rude habit of speech! Do you really think that such words should even come from a child's mouth?"

"It's just that...I got used to saying it"

"I see. Since you are a child, perhaps it is possible for that to happen."

Though A-Qing wasn't sure what she meant, for now, she nodded anyway.

"Haa. You are like a child left by the water. If you go into the secular world like this, your life will not last long."

"Me?"

"Didn't you already become enemies with the Yang Clan of Xinchang? The black-clad bastard beside him must undoubtedly be an assassin."

A-Qing seemed to know absolutely nothing.

After all, it was clearly visible in her utterly blank stare.

Ximen Surin sighed deeply.

"Haa. This foolish thing."

Her words were a bit harsh, but A-Qing understood the concern behind them.

So, she just tried to wear an awkward smile.

"By the way, that little child seemed to have eaten Shaolin's Great Rejuvenation Pill."

"Great Rejuvenation Pill?"

A-Qing asked back.

Such a reaction showed she had no idea what that was.

Ximen Surin laughed heartily.

"The Great Rejuvenation Pill is Shaolin's elixir, considered the greatest elixir under Heaven. It is said that it cannot be bought, even if a fortune is given. "

"Ah."

This was why Yang Xiaoyue had scammed her way to raising the price.

"Haa. Xiaoyue, that wretched girl."

"Eh, do you know Changming's mother?"

"How could I not know a child that was once a part of our family?"

The Divine Maiden Sect was a sect for women.

And according to the principles of the Divine Maiden Sect, one could never get married.

However, it was only human nature for people to want to see their own children, so they were still allowed to adopt a girl and raise her.

"Then, could it be that Changming'er is..."

"No. The baby is indeed that brat's daughter. After all, she fell in love with a man and ran away. "

"Ah."

Of course, that didn't mean the Divine Maiden Sect was an extremist feminist group that outright opposed marriage.

If they fell in love with a man and wished to marry him?

Then they simply needed to leave behind what they had received from the sect. In other words, they had to break their dantian and leave.

Ximen Surin wrinkled her face. 

"That bitch was full of greed."

Yang Xiaoyue ran away because she didn't want to follow such rules.

But she didn't just run away.

She thoroughly plundered the Divine Maiden Sects warehouse for a dowry.

Furthermore, she quite literally planned her heist.

She deliberately chose only the most valuable items and took them all.

That was why Chen Changming's past was so prosperous.

A-Qing was utterly incredulous. 

\textit{Huh, what the...I really didn't see you that way, Auntie.}

"She should have been pursued to the ends of the earth back then and presented an early death. She couldn't even let go of what was given to her. How could a despicable bitch who betrayed her own sect possibly live with great fortune after that? I should never have let her be."

That was the root of the problem.

Children born with Pure Yin Blood died before they turned twenty.

It was a divine punishment in the form of a terrible curse.

However, to a martial artist, this curse could also be the greatest blessing.

After all, it was the best quality one could have to become a Master.

Children born with the Pure Yin Blood could become Masters renowned throughout all under Heaven.

The problem was that it was nearly impossible to learn martial arts if born with Pure Yin Blood.

The body was frail and the energy was too strong, causing issues with forming the dantian, the very entry stage of martial arts.

"Then?"

"She needs the help of a Master. I am talking about the help of a true Master who has reached the Unrestrained Realm at the very least."

A Master who had reached the Unrestrained Realm could forcibly inject Qi through Qi Transmission, thus forcefully creating a dantian.

However, Qi Transmission required decades worth of a Master's Inner Qi.

"So, how could someone like that ever bring her daughter here? A wretch who violated the sects rules and ran away after stealing treasures."

That was why she fed her the Great Rejuvenation Pill.

If the pills medicinal properties could substitute for Inner Qi, a Master would not need to suffer any losses.

After all, it directly led to the formation of a dantian. Thus, no Master would feel burdened to take her under their wing.

"She must have been prepared to beg and even lay down her own life. She would've most likely pleaded to save her child's life at the cost of hers. That since the child had already consumed an elixir, she could be guided easily."

"Ah."

"That damned bitch! Since she had already betrayed her sect, how could she possibly know what attainment this Godmother reached?! There is no way she would've known! Ha!"

The Godmother had already reached Profound Realm a decade ago.  

She was now in a realm where she could control the overflowing and destructive Pure Yin Energy, thus being able to create a dantian.

There wasn't a need for Qi Transmission in the first place.

If she had just brought the child, the Godmother would have saved Chen Changming.

"It was unnecessary from the start, yet..."

If only she had known Chen Changming's Constitution and brought her immediately.

No matter how heinous her crime, the Godmother couldn't have killed the mother of the child she saved with her own hands.

And thus, the father would not have had to lose his life either.

Furthermore, the Lord of the Xinchang's Yang Clan would have eventually been injured whilst fighting the Demonic Cannibal, but the child would have already been rooted in the Divine Maiden Sect.

As such, the great clan that had long defended the East Sea against foreign invaders wouldnt have been scammed

"This is precisely what karma is. One evil deed plunged many into a pit of sorrow; such is the nature of Evil Karma."

Ximen Surin solemnly advised.

"So, Child, you must remember this well. Especially since you carry the most ominous star."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A-Qing didn't know anything about martial arts fiction.

Therefore, she was also unaware of the relationship between a teacher and a disciple in Zhongyuan.

In Zhongyuan, a teacher was akin to a master.

Essentially, a teacher was on par with one's parents.

But to a modern Korean, who did not distinguish between an educator and a teacher, the relationship between master and disciple was taken far too lightly.

This was the biggest reason why A-Qing so casually accepted becoming a disciple.

Moreover, A-Qing longed for warmth. She was starving for it.

It was natural for her to be completely taken by Ximen Surin, who exuded the vibes of a grandmother.

As such, A-Qing kowtowed deeply to Ximen Surin, accepting her as her teacher.

And then-

"If you go into Jianghu as you are now, Disciple's life will be in danger. It is highly likely to be cut short. Therefore, hiding your identity will be the priority."

"Hiding my identity?"

"Indeed. Disciple's face is already well-known. Moreover, since you have made enemies with a Transcendent Realm Master, you must reach the same realm to be able to live, much less plan your future. Until then, it is wise to hide your identity."

"Ah."

She hadn't thought about it that way.

The extent of her deliberation consisted of just fighting if it seemed easy and run away if otherwise.

After all, A-Qing was confident in her Movement Techniques.

"So, from now on, let's call you Ximen\footnote{lit. 'West Gate'} Qing (西門靑)\footnote{Fun fact: Ximen Qing (with a different 慶/ 'Qing' character) was also the name of the main protagonist of Jin Ping Mei/ The Plum  in the Golden Vase, a spin-off of Shuihu Zhuan/ Suikoden/ Water Margin. He's portrayed as a rich degenerate that's pursuing affairs left and right}."

"Men-Qing. Then, from now on, I'll go by Men-Qing. I'll share the same surname as Teacher, right?"

After all, whether it was Men-Qing or A-Qing, it was all the same to her.

Receiving a surname felt a bit burdensome, but since everyone in Jianghu seemed to use surnames, it would be strange to use only a given name.

{\itshape Then, am I now a Xi?

Come to think of it, I could have just used my original surna-}

THWACK!

"AHH!"

A-Qing screamed due to the terrible pain.

It was an uncontrolled screech that burst out instinctively.

It was a hydrogen bomb noogie, surpassing even the nuclear noogie.

{\itshape No, what the heck?

Couldn't it have split my head open? Isn't it bleeding?}

As A-Qing rubbed her head, she intermittently checked her fingertips.

\textit{Still, there doesn't seem to be any blood, huh. I thought there would be blood.}