\chapter{But You Said I Could Play Around? (14)}

Whether the veiled woman the warrior saw was the real Heavenly
Blossom Sword, he didn't know.

But she had been thrown out of an inn, lost consciousness, and was now
being unilaterally slaughtered by a wanderer, the veiled woman, and a
barbarian bitch.

So, rather than escaping, he turned around to report this grave situation.

Indeed, it was with a torn heart that he left his comrades behind.

Sahin's response was a palm raised high in the air.

The rogue warrior shrank his neck.

But a warrior wasn't a turtle, so his head didn't sink into his torso.

It was just an attempt to lessen the impact, but-

"Hmm. No. The idea isn't bad."

Sahin slowly lowered his arm.

Just as the rogue warrior was feeling relieved and was about to pull his
neck back out…

Slap!

A beat late, the sound of a slap echoed as the rogue warrior's head
whipped to the side.

"This is punishment for taking the Regiment Commander lightly. Do
you expect me to believe a story that even a dog wouldn't believe?"

"I apologize!"

Would an Orthodox Faction martial artist, especially one with the
martial prowess of a Transcendent Realm, use an assassin?

Moreover, if they sent an assassin, why would the client openly
associate with them and fight together?

However, the idea of using the Heavenly Blossom Sword as an excuse
was rather excellent.

It could serve as a justification to break the current stalemate, couldn't
it?

Whether she was the real Heavenly Blossom Sword or not, wasn't it too
harsh to take eight lives just for harassing a mere woman?

So, it was just about finding an excuse to pick a fight.

Thus, Sahin rushed to the leaders of the two high-ranking combat
regiments and spoke.

"Lately, that Heavenly Blossom Sword has been strutting around
Nanning like it's her own home, hasn't she?"

At this, the White Tiger Regiment Leader, Moon Jeongyeok, gritted his
teeth.

"Indeed. That damn bitch. She's only gotten cocky because she timed her
arrival with the Prince's visit. To think she dares to act so insolently in
the Fourth Disciple's territory."

"Ahem. Don't be so angry. That's precisely her scheme. In the
Romance of the Three Kingdoms, didn't Zhuge Liang provoke Sun
Quan to lead to his participation in the war? Provoking someone to
turn their stomach to achieve a goal. This is the very scheme of
provoking a general."

It was the military strategy of Jo Gwangang, the Infallible Tactician.

"That damn strategy talk. And what scheme would a mere child, not
even of age, have? She's just thoughtlessly playing around since she's
in a foreign land."

"Tsk tsk. She is a Transcendent Realm. Are you going to make the
mistake of underestimating your enemy? As the saying goes, know
your enemy, know yourself-"

"A hundred battles, a hundred victories! I know that too!"

"Tsk tsk, it's not a hundred battles, a hundred victories, but a hundred
battles without danger. If you're going to pick it up, at least pick it up
properly."

At Jo Gwangang's jab, Moon Jeongyeok's face flushed red.

Then, just at the moment when he was about to explode and shout
something…

Sahin opened his mouth at the perfect time.

"Ahem, I was actually bothered by that Heavenly Blossom Sword
bitch, so I instructed the Black Woong members to subtly provoke her
while on duty."

"Aha! Good! Why didn't I think of that? Why didn't I think of using the
scheme of provoking a general on our side? You have quite the mind
for strategy, don't you?"

Sahin's eyes twitched.

Even though there was a hierarchy between the Hundred-Class
Combat Regiment and the Black-Class Combat Regiment, Sahin was
technically the elder.

Of course, in a situation where both the regiment's level and his own
martial prowess were lacking, he was just an older person.

Still, to be addressed so informally.

That was why Sahin had kept his mouth shut.

"Since you've come here, does it mean you caught something?"

At least the First Sword of Bokju was a decent person.

Sahin opened his mouth again at that.

"So, it seems she was seen at an inn, and since there was a wandering
minstrel selling songs, they harassed her. Naturally, she drew her
sword in a fit of rage. And wouldn't you know it, she killed eight of the
Fourth Disciple's warriors."

Words have power, depending on how they are spoken.

It was the authority of a martial artist who had been active for over fifty
years.

The incompetent leader who lost eight of his subordinates due to poor
management had transformed into a cool-headed strategist who
sacrificed the lives of his subordinates to create justification and
achieved an unimaginable outcome.

At this, the eyes of the two Regiment Commanders lit up.

"She dared! To harm the Great Four Disciples!"

"She must be young and doesn't know how to hold back. She finally
shed blood, didn't she."

Despite eight deaths, Jo Gwangang chuckled and brought up a
strategy.

"If she drew her sword first, we have nothing to hold back. Let's blow
this up. Isn't the Prince at the Gyerim Sword School, and nowhere else?
If we start erasing some easy Orthodox Faction martial schools one by
one, the Gyerim Sword School bastards will realize that holing up
behind the Prince isn't the best option."

Moon Jeongyeok nodded and spoke.

"Hoo. Did you just say Prince? Then it seems you acknowledge the
result of the bet, yes? The Ever Losing Tactician, Jo Gwangang. A truly
fitting title."

Jo Gwangang's expression rotted.

At that, Moon Jeongyeok smiled satisfactorily and continued.

"Regardless, a colt that doesn't know the fear of the Jianghu's seniors
must be punished."

"Hmph. Can you even do it? I heard she killed the Flame Demon
Warlord?"

Jo Gwangang snidely remarked, feeling displeased.

"I hear she frequents the Yonggung Pavilion, right? If we get the
sewer rats to slip in some Incapacitating Fragrance or Numbing
Poison, that'll be the end of it. Let's ask Sasa for some medicine, hm?
But Sasa hasn't been showing his face lately, has he? Is he sulking
because that fun thing didn't work out?"

For reference, sewer rats was a term used by rogue warriors to refer to
the members of the Beggars' Union.

As Moon Jeongyeok said this, he looked at Jo Gwangang.

The one who sent the anonymous letter that caused unnecessary pain
to the disciples and cooks of Gyerim, Jo Gwangang, shrugged as if
asking, ‘Why are you looking at me?'

"Well. Anyway. If we bring in a crowd of spectators and humiliate her
by mentioning her sect, she won't be able to escape. So, what do you
call this in that strategy book you like so much?"

"Well, that's……"

Things that people do don't always fit neatly into a specific strategy.

As the answer was naturally delayed, Moon Jeongyeok teased him
gleefully.

"You're not answering right away, so you must not have read enough of
your strategy books, hm? If you can't answer immediately after reading
hundreds of times, shouldn't you read hundreds of times more?"

Jo Gwangang's expression crumpled.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Boyeol said he would wait five more days for Qing, but on the sixth day,
another letter arrived.

\begin{quotation}
	「Pig's Hour, Seokbongsil.」
\end{quotation}

Wow, only one line in the content!

If her ink hadn't run out, making the situation unavoidable, just seeing
one line in the letter would tell you that Boyeol was seriously upset.

But Seokbongsil?

So, if the room names are in the order of jewels, trees, flowers, insects,
or animals, then honeybee means it's another floor down.

Is the old man's wallet getting worse?

Well, whatever.

Qing thought as she tossed the letter into the furnace.

It would be nice to get another bottle of that Blood Coagulation
Poison, but I guess this is it.

The old man was a Demonic Adept, but he was surprisingly naive. If I
coax him a little, it seems like he might give it to me.

Then, Qing suddenly flicked her fingers.

Pig's Hour.

Sasa's Boyeol was extremely upset.

"This bitch is making a fool of me, on top of everything else. Does she
think I'm some sort of pushover? She had no intention of keeping the
promise from the start. What a wicked bitch."

It was an old man's specialty, talking to himself.

So, as Boyeol was pacing back and forth in the narrow room of
Seokbongsil, muttering ‘damn bitch, crazy bitch, I'll kill her if I ever
see her again', there was a knock.

Knock knock. At the sound, Boyeol shouted, containing his rage.

"Come in! You bitch, do you have any idea how much of a fool you're
making of me! I-"

Boyeol, who was about to burst into anger, paused.

It wasn't Qing, but a server from the inn.

"Ahem, what is it?"

"A guest from Yonggungsil asked to see you……."

The server, who was unnecessarily insulted, spoke with a trembling
voice, her shoulders shrinking before the Master's presence.

"A guest from Yonggungsil wants to see me? Who? And how do they
know who I am?"

"I don't know either, b-but a veiled guest specifically asked to politely
bring the elder staying in Seokbongsil……"

Who could it be, asking for him specifically while wearing a veil and
pinpointing Seokbongsil?

Boyeol headed to the top floor of Yonggung Pavilion.

The corridor's decor was already glittering with gold and adorned with
red silk and all sorts of ornaments, making it almost blinding even in
the middle of the night.

When he knocked on the door of Yonggungsil, the door opened, and
Qing greeted him with a gentle smile, not wearing her veil.

"Ah, you've come?"

"Hmph, you dare to summon an elder here and there. What kind of
manners have you learned, hm? This scent?"

A strong aroma of tea permeated Boyeol's nose.

"Since when should the great Sasa stay in a mere Seokbongsil? It
doesn't sit well with me, so I booked this room. You can rest here today.
Come on in, you're just in time. I was thinking of you, so I got some
Yukbo Chungsi."

"Ahem. It's not like I'm here to get treated to some tea."

The art of brewing tea was naturally included in Ximen Surin's
etiquette and refinement classes.

Qing's skill in brewing tea was ingrained through radioactive
infusion.

If she didn't do it, she'd do it perfectly.

Sasa, who was more passionate about tea than anyone else, could tell
just by the scent what kind of tea leaves were used and whether the
water had been brewed properly.

Qing carefully skimmed the surface of the water with the lid of the
teapot, a technique called Spring Wind Brushing the Face.

Boyeol held the teacup and looked at the tea.

It was part of the tea ceremony called appreciating the tea.

The temperature was good, the color was good, and the aroma was
good.

It was a perfect cup without any flaws, and Boyeol's lips loosened.

"Ahem, you've learned the art of tea quite properly."

"It's nothing, I still have a lot to learn."

After savoring three brews and enjoying the lingering fragrance,
Boyeol realized something was off.

The atmosphere wasn't right for getting angry.

"Ahem. But the deadline has passed, so why haven't you delivered?"

"Oh my, don't even get me started. They say it's one chopstick per
person, but they're putting five chopsticks with poison into just one
bowl of food. How am I supposed to poison anyone like that? It's not
even about the poisoning, the presentation of the dish is ruined from
the start."

"What?!"

"Also, do you have any internal disputes going on over there? I heard
someone sent an anonymous letter warning about poison. You didn't
send it, did you, Elder?"

"You and I are the only ones who know about this plan, so how could
I, hm."

Boyeol was about to ask how she could suspect him, but he suddenly
shut his mouth.

There was something that caught his attention.

These damn bastards, are they upset that this old man is trying to
accomplish something, so they're trying to interfere?

It wasn't like this operation was just for his own benefit. Wouldn't it be
better for everyone to finish quickly rather than wasting time stuck in
this remote countryside?

But they had to interfere like this.

"I see. So it was them. So even if someone else tried to poison them, it
would fail. So, um, if you happen to have another bottle……"

"What! Did you fail?!"

"It's not exactly a failure, it's just……"

Qing trailed off.

She couldn't exactly say that she hadn't done anything.

"But how could I have known that an anonymous letter would be sent?
There were five poison chopsticks……"

Qing made a pitiful expression and trailed off.

If Qing had gotten angry, he could have confronted her head-on, but
after having enjoyed the precious tea and feeling a bit guilty about the
anonymous letter, it was hard to say anything.

"This is really the last one. I have nothing more to give you. So you must
succeed this time. I'll give you another five days, so try to feed it to
them somehow."

Yessss. Three bottles.

Qing smiled and pocketed the Blood Coagulation Poison.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Meanwhile, the server who had been unnecessarily insulted by Boyeol
hurriedly went downstairs, not to the first floor, but even further down
to the basement.

It wasn't to hide and cry because she was sad about being treated like a
lowly person.

Rather, the server was part of a group that welcomed such treatment,
using her lowly status to engage in schemes.

They were the people of Jianghu, known as the Hao Sect.
