\chapter{But You Said I Could Play Around? (10)}

It was the Lantern Festival!

The word 'Wonso' meant the first night, using the characters for 'first' (으뜸 원) and 'night' (밤 소). It signified the day when the first full moon of the new year appeared, specifically the 15th day of the first lunar month.

Surprisingly, it had no relation to the Western word 'won' (一).

It was simply the holiday known as the Great Full Moon Day in Qing's homeland.

For the people of Zhongyuan, the Lantern Festival marked the end of the New Year holidays.

Since there was not much to do in the first month of the year anyway, people would eat, play, and revel since the Lunar New Year's Day. When the streets were brightly lit with lanterns symbolizing the full moon, they realized, 'Ah, today is the Lantern Festival.'

This realization signaled that today was the end of the holidays, the finale of the New Year's grand celebration.

However, Qing was more interested in the 'wonso' itself than the Lantern Festival.

Wonso was a type of sweet rice cake eaten during the Lantern Festival.

Usually, wonso was cooked in a soup to make 'tteokguk'(sliced rice cake soup ).

A type of tteokguk but with sweet rice cakes instead of the usual kind.

It was typically made with a clear broth and filled with sweet rice cakes containing sugar and sesame seeds or, depending on the region, red bean paste or sweet filling.

Clear meat broth with sweet rice cakes?

Qing shuddered at the atrocities of the Central Chinese people.

How could they… In the world!

How could they put sweet rice cakes in a meat broth!

Absolutely unforgivable!

Such a dish should never exist in this world!

Sweet rice cakes do not belong in a meat broth! This is just wrong on so many levels!

Therefore, they must all be eradicated!

With a burning sense of duty, Qing devoured the sweet rice cakes, determined to eliminate this abominable food from the world, sacrificing herself for the greater good.

It was a noble sacrifice, a sweet and salty sacrifice at that.

The Lantern Festival was a time to pray for abundance.

As she had cleared all the leftover wonso that the disciples didn't finish, wishing for abundance, her upper belly swelled up like a mountain.

"As expected of our Senior Sister! This Woon Aram has only managed to finish two bowls, but I cannot believe it! How can a human body possibly empty seven bowls of wonso! It's truly a miracle! It's truly astonishing! Look at that proudly towering belly!! It is a magnificent mountain that would make the Five Sacred Mountains of Zhongyuan bow their heads in shame! A skyscraper! A majesty that reaches the sky! This Woon Aram is deeply impressed!!"

As Qing lay sprawled out on the bed after a hearty meal, Woon Aram shouted excitedly beside her.

Qing felt a bit strange hearing that.

What the fuck? Does it sound like she's slightly making fun of me?

"Are you saying that with good intentions……?"

"Of course! Eating is a battle! And a battle is eating! What a person eats eventually makes up their body, so eating is the body! Is the body not one with food! Your strength, Senior Sister! I have glimpsed the secret behind it! It comes from your inhuman eating capacity! It comes from your superhuman ability to consume food!!"

"Sssssp. She seems to be making fun of me."

"However, this little girl Woon Aram!! I have a request for you, Senior Sister! May I, just once, touch that enormous food pouch with my own hands!? I can hardly believe my eyes is all!"

In truth, Qing was in a fairly good mood.

Her belly was full and her body was comfortable.

So if she wanted to touch her belly a bit.

"Gently. Don't press. I might throw up."

"What an honor! What an honor it is!"

With that, Woon Aram carefully reached out her hand and gently stroked Qing's taut, swollen upper belly.

Her touch was extremely cautious, like that of someone caressing the belly of a pregnant woman.

But then, her hand gradually moved upwards. As her fingertips gently and softly stroked, Qing couldn't help but burst out with a frivolous, "Kyaheuk!"

"Ah shit, Naram? That's not my belly, you know? Honestly, do you think the food I ate would be there?"

"Ah! Without realizing! These three peaks that are like mountains! I thought it was one mountain range! But since all the food is in your chest, is that not why you have such grandeur!"

Qing's eyes narrowed.

"You… You keep mentioning three peaks, don't you?"

"Ah, my apologies! I apologize! This Woon Aram will now perform the kowtow of apology!!"

Woon Aram immediately stood on her two hands.

But performing the kowtow once or twice was fine; after three or four times a day, it lost its impact.

But then, Woon Aram suddenly shouted desperately.

"Senior Sister! I'm sorry! Urk. I have eaten too much!!! I can't hold back the reflux. May I offer a regular bow instead!!"

"Sigh. You do all sorts of things, don't you."

Eventually, Woon Aram (thirty years old), kneeling with her hands raised, said dejectedly.

"This little girl speaks frankly, so I could not hold back my praise for Senior Sister's beautiful breasts. Senior Sister, if you were to take on a title, the Greatest Breasts Under Heaven would suit you best. Han people consider large breasts vulgar, but for us, the people of Jang, a woman's large breasts are the very definition of unsurpassable beauty. Moreover, your enormous majesty is not saggy, and the shape is beautiful as well. This Woon Aram, every time I see it, I am in awe, mystified, and feel a natural sense of respect. I cannot hold back this burning respect, so it just keeps spilling out……"

It wasn't a roundabout way of teasing, but rather a confession of her inability to restrain herself.

Well, having been together for a little over half a month, she had clearly seen that this athletic woman was not the type to make snide remarks.

She was just an overly enthusiastic middle-aged woman.

Thus, the night of the Lantern Festival deepened.

Surprisingly, Qing was now properly carrying out the mission of the Wulin Alliance.

Didn't even her Master tell her to go and have fun, rest well, and be treated well at the Gulin Sword Sect?

So it seemed like Qing was successfully completing her mission for another day.

But then, another letter arrived, disguised as correspondence.

\begin{quotation}
	「Do you even have any intention of keeping your promise?
	
	I will be waiting at the Peony Room at the Hour of the Pig.」
\end{quotation}

Today's activities were not yet over.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Today, the Dragon Palace Room of Nanning's top inn was overflowing with people.

It seemed like everyone was trying to let loose on the last day of the holidays, as every table on the first and second floors was full, with everyone enjoying themselves amidst the loud chatter.

"Hahat, Senior Brothers, this little brother will pour you another drink! On such a good day as this, how could it be any better, especially since I am with the Senior Brothers I respect the most? In that sense, may I offer a toast?"

"Of course, of course. How can we refuse a toast from our youngest?"

"Then, ahem. To the eternal friendship of the Virtuous Quartet of Qinghe!"

"To the Quartet!" "To the Quartet!" "To the Quartet!" "To the Quartet!"

Did you hear something familiar?

What the hell? Did the number change or something?

Is it just my imagination?

Qing tilted her head as she climbed the stairs.

Last time, the Dragon King Room Qing had taken was on the seventh floor.

The Plum Blossom Room taken by Sasa's Boyeol was on the sixth floor.

And the Peony Room that Qing was heading to was on the fifth floor.

What the hell? Is this old man a bit short on money?

Qing was slightly concerned about Boyeol's financial situation as she finally arrived in front of the Peony Room.

When Qing knocked on the door, a gruff, elderly voice came from within.

-What is it? I did not call for anyone.

"Why are you acting like this? You called for me."

At that, the door opened, and Boyeol, with an urgent expression, appeared.

Now, Qing's eyesight had reached a level where she could discern people's expressions.

It was a remarkable achievement.

"No, why are you here already? Quick, quick, come inside."

The current position of the moon was the beginning of the Hour of the Rat.

Qing had arrived a whopping one and a half hours earlier than the appointed time.

And she had casually walked through the guest room hallway.

"I mean, did you want to spread rumors that Sasa's and the Celestial Divine Sword were colluding? I told you it was the Lantern Festival, so people will be out late at night. That's why I said to meet at the Hour of the Pig. What on earth were you thinking?"

"What do you mean? Didn't you ask me if the Hour of the Pig was okay? I was going to go to the night market with Naram after this. Ah, do you know Naram? She's the Second Great Senior Sister of the Gulin Sword Sect. Anyway, I was going to look around the night market with Naram."

"What? No, what, what are you even."

It was a truly exasperating sound.

This was how Qing's tongue worked.

The more one talked with her, the more one-sidedly disadvantageous the structure became.

"Anyway, last time you were on the sixth floor, but now you're on the fifth? Doesn't the Yoga Flame Gang treat their elders too poorly? I heard you're a famous physician and martial artist. When people hear you're staying at the Dragon Palace Room, they should immediately give you the top floor, the seventh floor! And make it free."

"Oho! Yes, you're right. Since he's a salt-peddling bastard, he's stingy like salt. He said the plan might be prolonged, so even the food he's providing is starting to look worse. He has to feed me for a long time, so he's reluctant to keep providing expensive food."

"Isn't the Salt Gang rich?"

"That's what I'm saying! Anyway, this is why you shouldn't deal with those lowly salt-boiling bastards. A salt merchant calling himself a Noble Clan? Ha, I'm at a loss for words."

"I know, right? How dare those who just boil seawater call themselves noble when they don't even know the value of a physician? Especially a martial artist physician, who is ten times more valuable."

"That's what I'm saying! Ha, those ignorant sword-wielding bastards don't know the value of a physician. Even the bastards called Danju are the same. The other day, one of them…"

Boyeol poured out his accumulated grievances.

Qing responded with ‘That's right', ‘That's so wrong', ‘Amazing', ‘Really?', ‘How could such a thing happen' in a five-beat rhythm.

Thanks to this, Qing managed to gather various information about the approximate size of the Salt Gang and the dispatched combat units of the Sapaeryun, their martial prowess, the personalities of the Danjus, and other miscellaneous information.

"Ha, I can't believe I'm saying this now!"

Boyeol belatedly came to his senses after spilling out precious information.

When faced with the terrifying old woman slaughterer, both Great Experts and Demonic Adepts alike could not help but spill everything they had inside.

"No, if you made a promise, you should keep it. It's been half a month already. When exactly are you planning to administer the poison?"

"Ah. About that. Actually, I dropped it somewhere and I can't find it."

Qing offered the excuse she had prepared.

I dropped it somewhere (in my pouch) but I can't find it (because it's in my pouch, so I can't see it with my eyes), Qing rarely lied.

"What! Such a precious thing! You should have looked for it!"

"I'm sorry. Uh, so, do you perhaps have another bottle? Since I need poison to administer the poison…"

"Ha. Do you know how precious that poison is? It's a rare item that would cost more than ten gold ingots per bottle. Sigh."

"Ah. Is it that precious? As expected of one of the Ten Great Poisons Under Heaven. I'm so sorry…"

"Ahem, it's a poison that concentrates the venom of a thousand snakes in one bottle, so of course. Not just any venomous snake, but, well, never mind. Here. Don't lose it this time, no, just administer the poison as soon as you return."

"That's a bit… I have a prior engagement with Naram…"

Qing was going off on a tangent.

"No! If an adult tells you to do something, you just say yes!"

"But… The Lantern Festival is only today…"

"Haaa. Fine, four days. I'll give you four days. If there's no news of a death in the Gulin Sword Sect within five days, your true identity will be revealed to the whole world."

"Hmm, then could you add one more day while you're at it? The hand has five fingers, and when counting things under heaven, it's usually done in fives, so you should give me five days."

"Haaa. Fine, fine. Five days. I'll give you five days."

"Hehe. Thank you."

Of course, it was something to be thankful for.

After all, Qing had never said she would administer the poison.

She just said not four days, but five.

Sure? Then, add one more day and make it five.

Qing sometimes lied, but she always kept her promises.

Of course, she was also a vicious trickster who interpreted promises to her advantage.

Her skill at deceiving others was improving day by day. If she had used even half of this cleverness in her daily life, she would have avoided most of the dangers she faced.

Thus, an innocent old man was once again deceived by a con artist specializing in elder fraud.

And so, Boyeol was tricked again. 