\chapter{But You Said I Could Play Around? (13)}

A sudden attack of confession.

Qing replied.

"I don't want to."

"Oh my. Why not?"

At that, Wunam screamed.

"Of course!! That's obvious!! Isn't it!! Between women!! How!!! How obscene!!!!"

Qing, who had sensitive hearing, frowned.

It was a new record for Wunam's maximum volume.

However, Nayang Gyeol remained calm.

"Young Lady Ximen is a disciple of the Divine Maiden Sect, is she not? Surely, love between women is not unfamiliar to you? Ah, could it be that you already have a lover? Ah, could it be, the two of you!"

"Huh."

"Oh my! Senior Sister!? Y-You! You have been looking at me with those eyes!! I, uh, I! Th-That!"

Wunam blushed and averted her gaze.

"Senior Sister, if you give me a little time, th-that, of course, my respect for Senior Sister is like that of a mountain, but, th-that, if Senior Sister truly wishes it......"

Qing's eyebrows formed a steep curve.

"No way. Narami isn't my type either."

"Is it because my skin is not fair-"

"Ah, seriously. Why are you suddenly digging your own grave? Don't suddenly make me a Han chauvinist. And your complexion is so beautiful, Narami."

Han chauvinism was a dangerous ideology that considered only the Han people as the true owners of Zhongyuan, looking down on others as barbarians and inferior monkeys.

Of course, as people had lived together and mixed blood for generations, it was a trend that 'you, me, and us are all Zhongyuan, one Central Plains', so it was an ideology that was gradually losing its power.

However, for some reason, in Qing's homeland, a cruel Han chauvinist had been ruling as emperor for a long time, carrying out ethnic cleansing for the sake of a pure Zhongyuan.

He was even a paranoid Han chauvinist, to the extent that he had erased the Qipao (Cheongsam), a traditional Manchu garment, from all stories, calling it a foreign thing, and replaced it with traditional Han clothing.

At any rate, Wunam's eyes became moist.

"Senior Sister! Your massive! Gigantic! Vast chest! Its capacity! Your bosom is so wide! I, Wunam, although it is obscene! If it is Senior Sister!! This lacking body! Please take good care of meee!!!"

SMAAACK!!

With a sound like a chestnut bursting in a fire, Wunam grabbed her head and rolled on the floor.

She had tried to hold back from launching a nuclear strike out of consideration for her being an elder, but the unruly Aunt Narami had truly invited disaster upon herself.

Qing sighed deeply at Wunam, who was rolling on the floor with a loud scream, and then looked at Nayang Gyeol.

Nayang Gyeol was still smiling, looking at Qing with a blissful expression even after witnessing this horrific scene of nuclear devastation.

"Young Lady Na? Whether it's between women or men, who would nod at the suggestion of becoming partners at first sight?"

"But I fell in love at first sight."

"You don't even know what kind of person I am."

"I thought so too at one point, but, but, I feel happy just looking at Young Lady Ximen's face. I won't get tired of it even if I watch it for a thousand years. Perhaps, isn't my expression saying just that?"

In fact, Nayang Gyeol's expression was strongly asserting, 'I am happy'.

Unlike a certain group of fans who were full of anger, her expression was genuinely happy.

"So, Young Lady Ximen, why don't we take our time to get to know each other?"

"What's the point of marrying someone just because of their face? Wouldn't you just move on to someone prettier than me?"

"No. That's not it."

Nayang Gyeol firmly denied Qing's words.

And she continued.

"Because there is no woman in the world more beautiful than Young Lady Ximen."

So, she was not denying the part about moving on to a prettier woman.

Qing sighed deeply and shook her head.

"My goodness, Young Lady Ximen, do you know? Even that expression, as if looking at a hopeless piece of trash, is beautiful. How can you be so new and refreshing every time I see you?"

"......I'm going crazy. Seriously."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When entering someone else's home, it was customary to greet the owner.

And if a city was governed by a Prince, the entire city was practically the Prince's home.

So Jayu did just that.

"It's been a while, Elder Brother Suxi. The time we played together in the Eastern Palace is still vivid like yesterday. Is it not a pity how the years have passed?"

"At least you were cute when you were young."

"Yes. You were very fond of me."

A faint, nostalgic look passed over the brothers' faces.

A weak and timid person was, conversely, a warm person to someone else.

Especially to his younger brother, who was fourteen years his junior. This was also why Jayu had somewhat neglected security when going on incognito inspections.

"It is not a good time to reminisce about matters of the Imperial Palace, as there are many ears listening."

"Ah. Allow me to introduce you. This is."

Jayu pointed to the old man, Gyeon No, on his right and paused for a moment, before a sly smile spread across his face.

"He is a grandfather who serves me. He is also a master of the Unrestrained Realm."

"I greet Your Highness."

"This is a grandmother who serves me, and likewise, a master of the Unrestrained Realm."

"This lowly one greets Your Highness."

Here is a Transcendent who serves me, there is another Transcendent who serves me, and another Transcendent who serves me, and then a Peak Realm master who serves me, another Peak Realm master who serves me…….

"Stop. Why are both your feet on the ground? Why are you even opening your mouth to speak?"

It meant that if so many people were serving him, why was he even bothering to stand on two feet, and why wasn't he having them speak for him instead?

"Originally, there would have been five more to introduce in this place, but on the way, we were attacked by bandits, resulting in a tragedy. Unusually, these days, bandits wear silk clothes and are even armed with armor and crossbows. Oh, my, the world is truly becoming a dangerous place, is it not?"

"Hmm."

"So, don't you think that in such a dangerous world, one should have at least one means to protect oneself? As they say, one must take care of one's own body before anything else. That's why this younger brother is thinking of learning some martial arts."

At that, Prince Suxi's eyes widened in surprise.

It was forbidden for royalty to learn martial arts.

To be precise, it was forbidden for male royalty, excluding the Emperor, to learn martial arts.

There was no particular reason, just the obvious one that it could threaten the throne.

Therefore, royal women, who had no right of succession, would learn Fairy Arts for simple self-defense.

That was why the princesses were overwhelmingly superior in combat prowess, and it wasn't without reason that Jayu had been beaten up by Yeonseol when he was young.

At any rate, Jayu's statement that he would learn martial arts was essentially a declaration that he would reveal his rebellious intent.

"Deokhyun."

"Elder Brother Suxi. How long can we rely on someone else's mercy? Are you not afraid? Of the life where one day you wake up and think, ‘Ah, yes, shall I kill my younger brother?' or ‘I'm bored, shall I kill a younger brother for fun?' and your life is over just like that."

"Isn't that the price of being born with noble blood? The lives that live in this luxurious palace, eating well and dressing warmly, envied by others, are actually lives lived with a blade hanging over their beds."

"Then, what do you intend to do? Are you really suggesting we try a rebellion?"

At that, Jayu let out a deep sigh.

"I'm not saying to change the throne. If a blade is hanging over our heads, we should at least wear a helmet. If they try to kill us, we should at least be able to bite off a finger. We need to show our thorns so that we are not carelessly touched."

"Wasn't it such thoughts, such self-preservation, that called forth the eras of the Spring and Autumn Warring States, the Three Kingdoms at the end of the Han and the Jin, the Sixteen Kingdoms, and the Ten Kingdoms at the end of the Tang? The wars that submerged all under heaven in blood arose from each trying to preserve themselves. The heavens bestowed upon royalty the duty to govern the world, so how can we call for blood?"

"Brother, I did not blame you. Even though this younger brother was ambushed by bandits and almost crossed the threshold of the afterlife, and even though you sent an invitation to the Hongmen Banquet. I do not wish to blame you for doing what one must to survive. Just like me."

At that, Prince Suxi's expression clearly showed his guilt.

He had tried to kill his younger brother to save himself, so even if he didn't see his face, he knew he had done something he shouldn't have. Now that he was confronted with it, he felt even more ashamed.

"……I'm sorry."

"When you think about it, didn't you treat this younger brother really preciously when I was young?"

"It wasn't to that extent."

"So this younger brother is now repaying that kindness. Wouldn't it be really nice if your cute nephews took a rest in the mild lands of Sichuan? Especially since the eldest has become a Prince, he should rest when he can, even if he's busy with his studies."

"Deokhyun."

"And as I observed the martial artists, I thought, what a mystical study exists in this world. Flying like birds in the sky and cleaving rocks with a single sword, are these not the studies of immortals? I heard that I am already too late, but I think it would be a great opportunity for your precious nephews to become even more precious."

Give me your sons.

And I'm going to teach your sons martial arts.

Prince Suxi's face turned white.

"Deokhyun, that's too much, really, do you really have to go that far?"

"Hyung, I need to live too. But I don't plan on living alone. Let's all live together. Honestly, do you think that bastard will spare you just because you're stuck in this remote countryside?"

"If there's no difference between being killed or spared, he'll forget about it. Isn't he the type of bastard who can't see one thing if he's looking at another?"

"He'll kill if he needs to for that one thing. I sent a letter about the incident in Sichuan. That guy caused all that trouble just because he needed an excuse to say that martial artists poisoned me. Do you think he'll keep you safe forever?"

Prince Suxi's complexion was dark.

Then, he finally sighed deeply.

"Let the sons stay. Aren't they your nephews too? If you still have any lingering affection from the past… I'll learn martial arts instead."

"I still vividly remember how well you treated me. I'm grateful to you, Hyung. But, which do you think is safer, Sichuan or here?"

"But learning martial arts is… Isn't that being a complete traitor?"

"Look at you now. Do you think the imperial family will do anything just because we have Masters? The army is far away and there's no way to protect ourselves from the blades and spears right in front of us. Learning martial arts seems good, that's my sincere opinion. At least we should have a way to escape."

Prince Suxi shook his head.

"So, do you have a way to ensure our safety as you suggest?"

"There's a field of gunpowder. The yield is good. We already have over 80,000 geun."

At this, Prince Suxi's expression turned to one of shock.

"You, you were really a traitor."

"For now, keep your nephews here, and Hyung, you should be careful. Um, first, eliminate the spies in the royal household, and it would be good to bring in some mercenaries."

Suddenly, Qing's image flashed through Jayu's mind.

If there is grace received, it must be repaid.

"Among the martial artists, those who call themselves the Orthodox Faction are quite trustworthy. Since the Embroidered Uniform Guards or eunuchs might try something, try to nurture some of them to use. They are the type of people who value honor like a thousand gold, so they should be easy to handle."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"What!? What did you say!? Say that again! Say it!"

Hyuju's Flying Tiger, Sa Heun, had a great title, but Hyuju wasn't exactly a prosperous city.

He was the type of martial artist that skilled people would mockingly call the Neighborhood's Number One.

However, skilled people can make fun of him.

But for the weak, he was an expert who was out of reach, so it was natural for the Black Bear Squad warrior to tremble.

"Th-There was a simple gathering, but suddenly some bitch ambushed us. R-Right! An assassin! It must be an assassin! How could a mere wandering entertainer be so strong otherwise-"

Slap!

The warrior's cheek was flung to the side.

At fifty-five, a martial artist was no idiot.

He immediately understood what the situation was upon hearing about it.

These stupid fuckers must have harassed a wandering entertainer, and the problem was that the entertainer was a Master.

Even though he emphasized over and over again to be careful of young children, women, and old people in Jianghu, they just never listened.

"Okay, was it an entertainment troupe or an entertainer?"

"E-Entertainer, it was an entert-"

Slap!

The warrior's cheek was hit once again.

"You're saying you were beaten by one woman? And you're the only one who managed to barely escape alive?"

"Th-That, uh, no, there were more!"

The warrior desperately tried to come up with an excuse, when he suddenly thought of a plausible one.

"Veiled Swordswoman! That's right! It must have been the Veiled Swordswoman! The Veiled Swordswoman hired an assassin to ambush us, and then she killed my brothers!"
