\chapter{But You Said I Could Play Around? (6)}

New Year's Day!

Qing was more familiar with the name Seollal(Korean New Year), which was truly the greatest holiday of the Chinese people.

Of course, even if one was not Chinese, there was no ethnicity that did not celebrate the passing of one year and the welcoming of a new one.

In the past, long ago, there was a monster called Nian (年兽) with a large horn. It was said that on the day the year changed, this monster would crawl into the human world and eat people.

However, this monster was most afraid of the color red, lanterns, and loud noises.

Thus, to chase away this monster, the Chinese would stick red paper on their doors, fill the village with lanterns, and make loud noises by banging bamboo together when it was New Year's.

Then, what happened after gunpowder was invented?

Gunpowder creates light, and light drives away monsters with a mighty roar.

This fact was even depicted in the Subakdo.

Therefore, before the first day of the new year, the land of Nanning was bright as thousands of lanterns illuminated the streets.

For the few days of the year when it was legally permitted to enjoy the nightlife, drinkers were already heavily intoxicated and boisterous, children were giggling and playing, beggars were full for once and sprawled out, lovers held hands, and married men, surrounded by their wives and concubines, strolled the streets.

Even lonely men and women were daring enough to reach out their hands at this time, making it a night full of abundance, joy, and fertility on the cold earth.

However, there were those with twisted personalities who found the sight of commoners enjoying this one day of the year unsightly.

‘Don't enjoy yourselves!'

Although they did not utter it, their eyes, which seemed to say they would kill anyone who dared, held such a meaning.

These were the warriors of the Salt Merchants.

‘Why, oh why, oh whyyyyyyy, did it have to be me? Why did it have to be me, of all fucking people, huh?!'

‘What the fuck is this? Some of us have to risk our lives on New Year's Day.'

‘The kids are playing, and those kids should all burn in hell. Those couples holding hands and about to fuck should all burn, that laughing bastard and that drunkard should all be burned to ashes.'

Of course, the warriors of the Salt Merchants had some issues with their personalities.

But still, it was understandable to an extent.

After all, they were about to take the lead in the upcoming battle, which was another way of saying they were the first to be served as sword fodder.

So naturally, their nerves were on edge, and they were thinking, ‘On this wonderful New Year's Day, will I be able to survive? I must see the morning sun alive,' as they steeled their determination.

Of course, these were the thoughts of the low-ranking warriors.

Three combat units belonging to the Four Great Evils followed behind the Salt Merchant warriors, and whether it was sincere or just a bluff, they were chattering about how seeing blood as soon as the new year began was a sign of great fortune for the coming year.

It was the advance of the Salt Merchants.

It was truly a villainous act worthy of those belonging to the Unorthodox Faction.

Logically speaking, who would attack as soon as the year turned just because the deadline was set for this year?

But surpassing common sense was a strategy of war, or so claimed the White Lotus Iron Fist Jo Gwang-ang, the leader of the White Bear Unit, a combat unit under the Unorthodox Union.

It wasn't that there were no objections.

But Jo Gwang-ang sank all opposing opinions with a single sentence.

‘What, are you afraid?'

In Qing's hometown, it was the ultimate technique of a man, often referred to as ‘Yo, you scared?', and was a major cause of accidents, including minor and major injuries.

Thus, the Salt Merchant Leader Yo Hwanjeol and the experts of the Unorthodox Union took the lead, followed by the grim-faced general members of the Salt Merchants, and behind them, the dispatched combat unit of the Unorthodox Union kept an eye out for anyone trying to escape.

And so, the eve of the decisive battle, no, the very night of the decisive battle!

Yo Hwanjeol headed towards the manor of the Guilin Sword School, which would become the new foundation of the family.

The Guilin Sword School bastards must have never imagined that they would be swept away so quickly.

If they had received word, they would have hurriedly closed the gates and gathered their disciples, but in front of the Salt Merchants' elite warriors (as claimed by the Salt Merchant Leader) and the reinforcements from the Unorthodox Union, they would be swept away without a chance to react.

"Hmm?"

But lo and behold.

Far from preparing for battle, the manor's huge gates were wide open, and it was brightly lit with lanterns all over.

Peering inside, a feast was already in full swing, with everyone laughing and having a good time.

Yo Hwanjeol, Jo Gwang-ang, and the other experts exchanged glances.

‘What is the meaning of this?'

‘How should I know?'

Moreover, not a single guard was posted at the wide-open gates, which meant that they were welcoming anyone to enter without reservation.

At this point, they were utterly dumbfounded, confused, and at a loss for words.

They should have been gloomy, thinking they would soon be kicked out, or already fled in the middle of the night, or at least shown a dignified spirit to fight to the death. But what was this feast all about?

"Indeed, you can't spit on a smiling face! The Guilin Sword School bastards must be plotting something!"

The self-proclaimed military expert, Jo Gwang-ang, was convinced and admired all on his own.

"They think that we won't dare to attack if they show a carefree attitude, laughing and enjoying a good day, but heh, how naive. The path of the Four Great Evils is the path of might. Compassion is nothing but a luxury. We walk the path of Asura!"

The White Bear Unit Leader, Jo Gwang-ang, arbitrarily shouted.

The Black Bear Unit Leader, Hyejubiho Sahm, and the White Tiger Unit Leader, First Sword of Bokju, Mun Jeongyeok, had never agreed to walk the path of Asura, but whatever.

Following Jo Gwang-ang, who had unilaterally decided to walk the path of Asura, the Salt Merchant Leader, the two Deputy Leaders, the three Unit Leaders, and other notable figures rushed through the gates.

Then, in the largest prepared seat facing the front of the spacious manor yard, the Guilin Sword School Leader, Gang Suyang, acted surprised.

"Oh my, isn't that the salt-selling Yo? What brings you here?"

He called him a salt-selling Yo right off the bat.

And he was asking what business a lowly salt merchant had here.

From the very first sentence, Gang Suyang was successfully turning Yo Hwanjeol's insides upside down.

This was the way of the Orthodox Faction.

Since it was uncouth to outright curse, they always strived to insult indirectly.

In this regard, Qing was more of an Unorthodox Faction member. No, she was actually a venomous witch of vicious slander who was wicked even for the Unorthodox Faction.

"Ah, you came to pay your respects. Well, since you're here, you should offer a drink. Yes, of course you should."

"Who! Who said anything about paying respects!"

"Hmm? You didn't come to pay your respects? I thought you brought all your warriors to do just that."

"Stop with the nonsense-"

"Enough!"

Suddenly, Jo Gwang-ang cut off the Salt Merchant Leader's words.

The Salt Merchant Leader, Yo Hwanjeol, was taken aback.

Even if he was a Master of the Four Great Evils, he was still the leader of a faction. How could he just cut off his words like that? What would happen to his dignity?

Although the Salt Merchant Leader was deeply offended, if the person in question didn't care about such things, he wouldn't have cut him off in the first place.

"Haha, it seems the Sect Leader is trying to avoid a disaster with a clever trick, but you should read more military strategy books. After all, a clever trick is helpless against the orthodox method, and Sun Tzu emphasized that the best defense lies in preparation. A force that is always ready for battle is the true defense."

At that, Gang Suyang looked at Jo Gwang-ang with a blank expression, as if to say he had no idea what he was talking about, but decided to listen anyway.

"Haha, are you flustered because your Sect's desperate ploy has been seen through? But there is no need to be too disheartened. You do not have to be ashamed that you were outwitted by this White Lotus Iron Fist Jo Gwang-ang, who is widely known for his ingenious strategies."

At that moment, Qing's eyes lit up. One, two.

"White Lotus Iron Fist!"

Qing suddenly shouted loudly.

Her voice was not just loud, but incredibly loud.

As the puzzled gazes of everyone in the area gathered on her, Qing broke out in a cold sweat.

Ah shit, it seems like there are some rules shared among locals when shouting out monikers. It seems like now wasn't the time.

"Uh, um……, I just thought I heard it somewhere before. Um, please continue the conversation you were having. Ah, this, I wanted to eat this, my favorite, um, what soup, yes, um, soup, it looks delicious."

"Senior Sister? That's not soup, that's oil skimmed from the hot pot-"

"Shh. Mind your own business."

Qing awkwardly spoke up, took a spoonful of the oil that had been skimmed off for later use in cooking, and said some nonsense like, ‘Hmm, this is the tastiest as expected. It's so oily because it's oil,' trying to create a natural atmosphere.

Then, Jo Gwang-ang thought.

What a foolish woman. Anyway, moving on.

"Ahem, ahem. Anyway, Sect Leader. Clever tricks are just that, clever tricks. Once a man draws his sword, he cannot turn back. So instead of leaving a foolish record of being caught off guard while enjoying a feast in the face of an enemy attack, you should now-"

Jo Gwang-ang was boasting for a long while.

Suddenly, a clear and resonant voice, filled with profound Inner Qi, shook the surroundings.

"His Highness arrives! His Royal Highness Prince Deokhyun is taking his seat, so greet him with the utmost respect, as you would your own father!"

At that, the disciples of the Guilin Sword School, who had made prior arrangements, immediately stopped enjoying the feast and assumed a respectful posture, kneeling.

Since the Guilin Sword School disciples had already greeted the arrival of the Prince, they only needed to kneel and show respect, as greeting the same person twice in one sitting was forbidden.

The Salt Merchant Leader and the other experts were greatly taken aback.

A Prince? A Royal Prince? Suddenly?

What is this bolt out of the blue?

At that moment, Jayu emerged from the main hall and sat in the highest seat behind Gang Suyang.

It turned out that there was a seat one step higher behind the highest seat, where the most honored guest was to be seated.

Then, placing his elbows on the table and propping up his chin, he spoke.

"Hmm? What is this? Who are those people standing so stiffly in the presence of the bloodline of the Son of Heaven?"

"Your Highness. That fellow in the front is a salt seller called Yo, and it seems he has come to pay his respects upon hearing that Your Highness has arrived."

"Oh, is that so? I thought I heard someone raising their voice, asking who said anything about paying respects?"

Yo Hwancheol turned pale.

‘You crazy bastards! You asked me to empty the manor, but you invited a fucking Prince?! Do you not know the rule of not touching government officials, you cowardly fucks?!'

The clock hadn't even struck midnight yet.

The old year hadn't even passed. And yet, this was the thought of the one who had invaded.

However, spite was spite, and a living man had to live, right?

"No! I have always most admired Your Highness and came to pay my respects! Your Highness, Happy New Year!"

Yo Hwancheol paused in the middle of his bow.

It was because of the Guilin Sword School Leader, Gang Suyang, who was sitting right in front of the unknown prince.

If he bowed as he was, it would look as if he was bowing to Gang Suyang as well.

"Hmm, Sect Leader. Is this how disrespectful the manners of martial artists are? Even if he is of royal blood, he cannot simply bend his knees?"

"No! Long live the Emperor, long live, long live a thousand years!"

Yo Hwancheol threw himself to the ground, raising both arms and shouting ‘Long live the Emperor'.

Jayu's gaze turned to the still bewildered experts dispatched from the Unorthodox Union.

"Bo Mo of Jianghu greets Your Highness! May you live ten thousand years!"

"Hwa Mo of Bokju greets Your Highness!"

"Sa Mo of Hyeju greets Your Highness!"

"This is Jo Gwang-yang of Hyeongyang! May you live long!"

Starting with Bo Yeol, the experts of the Unorthodox Union hurriedly threw themselves to the ground.

Dealing with the manor was one thing, but the place where the Prince resided was the sacred area of Zhongyuan.

"Yes. Although the new year is still a bit away… I wish you all a happy new year as well. Hmm, but there seem to be many people outside."

At that, Gang Suyang readily replied.

"They are all people who have gathered on this fine night to pay their respects to Your Highness, are they not?"

"Is that so? They are truly commendable. But if I were to receive their greetings one by one, this fine night of New Year's Day would pass. Alright, it's on me. I shall go out in person to receive their greetings."

Thus, the benevolent Prince Deokhyun personally went outside to greet the gathered well-wishers.

"Long live His Highness, Prince Deokhyun! Long live, long live!"

"Long live His Highness, Prince Deokhyun! Long live, long live!"

Moved by this, the martial artists of Jianghu simultaneously pressed their knees, elbows, and foreheads to the ground, shouting the noble title of the Prince until the world seemed to tear apart.

All of Nanning resounded with their deafening cries.
