\chapter{ButYou Said I Could Play Around? (9)}

Ziyou was, in a sense, already dead once.

If it hadn't been for Qing, he would have either burned to death somewhere in the midst of the inferno, been slaughtered by the soldiers beforehand, or, if he had been incredibly lucky, how likely was it that a frail scholar would have survived the wilderness?

Why did this happen?

Ziyou gritted his teeth in resentment.

There was no way that information about his secret journey to Guangxi Province to seek an alliance could have leaked from Prince Dexian's residence.

After the incident in Sichuan, discipline had been thoroughly enforced.

Moreover, they had delayed the announcement of his departure for as long as possible before setting out.

So even if, by some chance, there were still spies within Prince Dexian's residence, there wouldn't have been enough time for the Emperor to mobilize the northern troops and set up an ambush.

However, there was someone who knew about Ziyou's secret journey in advance.

It was Prince Shushi of Nanning.

Prince Shushi must have informed the Imperial Court of Ziyou's secret journey, and the Imperial Court, seeing an opportunity, mobilized the troops.

Considering the time it would have taken to mobilize the troops, he must have reported it immediately upon receiving the letter, without a moment's hesitation.

Ziyou had clearly written in his letter, ‘The Emperor's attitude is extremely dangerous. I cannot guarantee the safety of the Princes.'

Was there any loyalty left for the Emperor?

Or perhaps, since Guangxi was a barren province with a sparse population on the border, Prince Shushi thought that he wouldn't be affected, thinking of it as someone else's problem.

If so, then he should be made to realize that it was no longer someone else's problem.

Ziyou was already half a traitor.

He was cultivating gunpowder in Sichuan, and the Tang Clan was continuously producing powerful artillery shells, poison shells, illuminating shells, and many other potent weapons.

However, he couldn't just sit and wait for death.

If the Emperor desired his death, he couldn't just willingly give up his life. To survive, he had no choice but to fight back.

Brother Shushi, please have a taste of treason.

It's more comfortable than you think.

However, if Prince Shushi had been in communication with the Imperial Court, entering Nanning without any countermeasures would be dangerous.

He could either hide somewhere and wait for his subordinates from the Prince's residence to arrive, or he could openly make his arrival known to all the citizens of Nanning, so that Prince Shushi couldn't touch him recklessly.

That was why Ziyou had made a grand entrance during the new year, receiving a large-scale welcoming ceremony from the Four Faction Alliance.

For the people of Zhongyuan, watching martial artists fight each other was the light, the salt, and the greatest joy of life.

Thus, the citizens of Nanning, who had been following behind the Four Faction Alliance, ended up paying their respects to Ziyou along with the martial artists of the Four Faction Alliance.

Thanks to this, the news of Ziyou's arrival spread throughout Nanning.

After all, those Four Faction bastards, who seemed ready to kill each other, collectively bowed and then listened to his well-wishes on their knees before stupidly retreating, had they not?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Although it was not Ziyou's intention, the Four Faction Alliance had become quite a laughingstock.

Yan Fangju, Yo Hwancheol, was anxious, facing a major obstacle ahead of his lifelong ambition.

The leaders of the three combat units also couldn't just challenge the Prince.

However, the old man Sasa Boyeol kept chuckling ominously, saying that there would be something fun soon.

"What exactly is this fun thing? Let's hear it together."

"If you watch, you'll know. It's no fun if you know in advance. Hehe. If I had to give a hint, it's that a snake that quietly slithers into the bedroom is dangerous."

The leaders' expressions soured.

A hint, my ass. He's just itching to talk about it.

A snake that quietly slithers in basically meant he was saying everything.

Whoever was bribed, they were attempting to poison him by some means, and they were confident in their success.

For reference, that deadly snake, the one that was supposed to quietly slither into the bedroom, was currently hiding its fangs and enjoying a hot spring bath.

And she planned to continue enjoying it tomorrow and the day after, using the excuse of recovering from her injuries.

Sliiide.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"No, why is that son of a bitch, Dexian, doing this!"

The man with drooping eyebrows, giving him a particularly weak impression, burst out in anger.

A person's face tends to settle into the expressions they frequently make. Considering that, even someone who was not a physiognomist could guess that Prince Shushi's character was originally timid and weak.

That was why he was out of favor with the previous Emperor, hence becoming Prince Shushi.

"He should die alone if he wants to die, why drag me into it!"

"Your Highness. You must make a great decision."

The man beside him was the Chief Administrator of Guangxi Province.

Originally, the Chief Administrator was the highest authority in a province.

However, in a province ruled by a Prince, he was a scarecrow who couldn't do anything at his own discretion, having to ask for permission even to breathe.

Therefore, the Chief Administrators of Guangxi Province, who had been completely stripped of their power, were actually happier than ever! This was great! Being a scarecrow was the best!

This was the general opinion of the Chief Administrators.

They could receive a hefty salary without any work or responsibilities, just playing the role of an advisor while greeting the Prince. It was the sweetest of gigs.

"A decision?"

"If the Hegemon-King hadn't held a banquet for the High Ancestor, the ruler of the world would have changed."

He was referring to the Hongmen Banquet, where Hegemon-King Xiang Yu invited High Ancestor Liu Bang, intending to kill him.

However, Liu Bang, who had realized the intention, fell at Xiang Yu's feet and said, ‘Brother, brother, your little brother has come! Your little brother, who respects you the most in the world, is here! What can I do for you? Just say the word, and I'll even give you my wife. Ah, there's dust on your shoes, stay still, this little brother will clean it with my tongue!' He flattered Xiang Yu so much, almost licking his butthole raw.

At this, Xiang Yu thought, ‘I can't kill this lowly flatterer. What would my reputation be if I invited this kind of guy just to kill him?' So he decided not to kill him.

The fierce clash of strategies, sword dances, and wits between the vassals during this banquet was considered one of the highlights of the Records of the Grand Historian.

It was a famous scene, holding a position similar to the Three Visits to the Thatched Cottage in the Romance of the Three Kingdoms.

The Chief Administrator's suggestion was referring to this scene.

Since he had come to Nanning, he should be invited.

And then, they would take care of him.

"Hmm, that's a bit much."

"Your Highness, Prince Dexian is already out of favor with His Imperial Majesty. Haven't you heard that the fire demon has struck? Why do you think it struck? Don't you know that His Imperial Majesty is someone who does what he says?"

The last remark was indirect, but it essentially meant, ‘Don't you know that old man is a dirty, ill-tempered bastard?'.

If he got on his bad side, it wouldn't end with just a fire demon.

A shadow fell over Prince Shushi's face.

"I just wanted to live quietly."

Why else had he volunteered to go to the remote area of Guangxi Province?

It was simply to live a quiet life.

If he had known it would be like this, he should have asked to go to Yunnan or Qinghai.

However, Yunnan and Qinghai were really too rural and remote, so he had chosen Guangxi Province as the bare minimum for human habitation.

"Hold a banquet and send an invitation. But, the invitation……"

Then, Prince Shushi's brow furrowed.

Do I really have to send an invitation?

Even though I reported him to His Imperial Majesty, I never imagined he would try to kill him by mobilizing even the fire demon.

I just thought he would be captured, maybe get a warning, or at worst, be confined to the palace in Beijing.

But he came into my territory and didn't even show his face.

He didn't even send a letter of greeting.

Prince Shushi, unable to think of what he had done, felt resentful for no reason.

Thus, an invitation was sent to Prince Dexian.

\begin{quotation}
	「I'm sick, so I can't go. Hehe, sorry.」
\end{quotation}

And the reply that came back was Ziyou's response, which could be summarized in one line.

This son of a bitch!

Prince Shushi's face contorted in anger.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Moon Jeong-yeok secretly sought out Jo Gwang-ang.

"Hey, Eternal Losing Strategist."

"Hmm. What's this? Are there mosquitoes in winter?"

Jo Gwang-ang pretended not to hear.

Moon Jeong-yeok, with a sour expression, spoke again.

"Hey, Jo Gwang-ang."

"Why are you calling me?"

"Are you going to be this petty? Are you not accepting the result?"

The bet was Moon Jeong-yeok's victory, the number one swordsman of
Fuzhou.

A few days had passed since then, and the Gulin Sword Clan no longer needed to set up guards at every entrance, large and small.

The soldiers of Guangxi were now taking turns standing guard.

If he were a fake prince, there would be no need for soldiers to be spread out to protect the Gulin Sword Clan.

"The circumstances suggest he's likely real, but it hasn't been clearly proven that he's real."

"What, does the military strategy book tell you to insist you didn't lose like that? I didn't think highly of Son Mu before, but he was a remarkably petty person, huh?"

Son Mu, also known as Sun Tzu, was a revered figure in China, with ‘Tzu' being an honorific title for great sages.

"In war, nothing is off-limits-"

"Enough. What does your beloved military strategy book say? When you've worked hard and spent time to almost conquer a fortress, only to have some random guy about to snatch it away right before your eyes."

"Hmm."

Jo Gwang-ang recalled the military strategy books he had read.

However, the teachings of military strategy books explained how to snatch away a fortress when some random guy was about to conquer it, not how to defend against such tactics.

"Hmph. Military strategy books are all useless."

"No, wait, there's the saying, ‘Enemies on the same boat'! Enemies on the same boat, there's that!"

Jo Gwang-ang suddenly shouted.

It referred to the people of the enemy nations Wu (not that Wu) and Yue riding the same boat, meaning to temporarily join forces against a common enemy.

"That old man Boyeol will probably use poison. He's always been one to say that a snake that quietly slithers into the bedroom is dangerous, but what is there to fear from a snake if you know it's coming?"

"So, you're saying we should warn the Gulin Sword Clan?"

"What's wrong with that? If we send an anonymous letter, who will know who sent it? And once you're prepared for poison, there's nothing to fear."

It sounded plausible.

However, Moon Jeong-yeok soon shook his head.

"Now that I think about it, I don't see the need to go that far. They're part of the family anyway, so we can just concede some credit. And even if we stop the poisoning, the Prince will still remain, so it's not like we have a solution. I'll just drink with my subordinates and go back."

"What? Are you not angry? You didn't even call some random person, you called me. If I can't eat it, no one else can. I can't stand this. No, I won't stand for it."

Jo Gwang-ang gritted his teeth as he spoke.

"Well, you're better than that old man Boyeol, at least. So I won't hear of it. I heard nothing. What were we talking about?"

Moon Jeong-yeok, inwardly cheering, carefully concealed his sinister intentions.

What a simple-minded fool. He's practically jumping with joy at just a little push.

And so, that snake was currently enjoying a hot spring bath with the unsuspecting First Apprentice Sister, completely unaware.

And for ten days straight.

It was truly diligent attendance.

"Elder Sister! Aren't you tired of the hot springs? If you're a martial artist, you should love mountains! And if we're talking about mountains, we should be talking about Green Crystal Mountain! And if we're talking about Green Crystal Mountain, we should be talking about Nanning! Shouldn't we loosen up these muscles that are so relaxed they're practically melting!"

"Mm, no. I'm not tired of it."

"Is that so………"

Woo Naram's spirits, which were usually so high, dampened for once.

It was a rare sight that would have surprised the disciples of the Gulin Sword Clan.

"I'm a patient, you know. A patient."

"Green Crystal Mountain is fine! The highest peak is not even a hundred zhang1, it's just a low hill! It will definitely help with Elder Sister's rehabilitation!"

"Mm. I appreciate it."

Having been together for over ten days, Woo Naram was someone who couldn't stay still.

Even in the hot spring, she would splash around, go out of the bath to swing her arms and legs around, suddenly demonstrating martial arts moves, and then come back in when her body cooled down in the cold winter air.

Judging from this temperament, she seemed to enjoy hiking.

Suggesting they go to a hill instead of the mountains with clouds in their waist to the west was probably her consideration for Qing's injuries.

But hiking was a bit, well… Especially in a low mountain.

There was no particular reason to seek out low mountains in Zhongyuan, as even in Qing's homeland, the mountains, though gentle in terrain, were beautiful in scenery.

After ten days of playing and eating, or perhaps due to the actual effects of the hot springs, or maybe because of Qing's incredibly fast recovery, the swelling on her side had reduced by half.

At this rate, it seemed like she would be fully recovered in about fifteen more days of rest.

And her vision had recovered to the point where she could read text at close distances without issue.

"Since it's been ten days, shouldn't I be fine now? What did you say again? Daemyung Mountain?"

"You know of Daemyung Mountain! If it's Daemyung Mountain, it's Nanning! And if it's Nanning, it's Daemyung Mountain! And if you're going south, there's Yilingam! If you haven't seen Yilingam, you can't say you've been to Nanning!"

"Sure, sure. Once my body is fully healed, let's do everything our Naramie wants to do."

The official age of twenty-one, Qing, said.

To which, our Naramie, with the official age of thirty, replied.

"Yes! Elder Sister! This little girl! I'll be looking forward to that time with bated breath!"

After that, another day passed. As Qing soaked her wrinkled hands and feet and giggled, she returned to the Gulin Sword Clan.

Welcoming Qing, who had entered the guest quarters, was another love letter from Sasa Uieui.

\begin{quotation}
「When exactly are you going to keep your promise?

Do I really have to reveal your true identity to the whole world?」
\end{quotation}

Qing snorted at this.

Reveal it if you want, or don't.

Qing tossed the letter into the fireplace. 