\chapter{But You Said I Could Play Around? (3)}

Flap, flap. A pigeon, without any fear, easily flew over the high walls of Grand Prince Deokhyun's manor and landed inside.

Of course, no one would get angry and shout, ‘How dare you fly into the manor without permission! Even if you are a mere beast, I cannot forgive you!' just because a pigeon flew into the vast estate.

After all, it wasn't as if the pigeon would politely knock on the door with its beak and say, ‘I may be a nameless bird without parents, but I have heard of the renowned virtue of Grand Prince Deokhyun and wish to visit. May I enter, coo, coo.'

However, this pigeon was a bit special.

It was a pigeon trained to find and fly to the manor no matter where it was released in Zhongyuan.

If it survived attacks from birds of prey, wild dogs, feral cats, and the most dangerous predator of all, hungry beggars, it would eventually return to its perch in the manor. It was a messenger pigeon.

Thus, the pigeon keeper of the manor expressed his delight upon seeing Yeongsun-i (Pigeon, six years old, coincidentally sharing the same name as the kitchen's handmaiden he secretly admired) suddenly return.

"Oh, Yeongsun-ah, what a surprise! Did you come back because you missed your big brother? Where-"

The keeper, who was chattering away as he tried to remove the message tube attached to the pigeon's leg, paused.

The message tube was covered in blood.

At this, the keeper hurriedly opened the message tube.

The trained messenger pigeon pecked hard with its beak to protect the tube, but the keeper didn't even have the mind to feel the pain.

No, it can't be. There has to be a message.

But the message tube was empty.

The keeper's complexion turned pale.

This was the most urgent type of distress signal.

The sender had quickly stained the pigeon with blood and sent it flying, indicating that there was no time to write a message and that the Grand Prince's life was in great danger.

The keeper rushed out of the aviary.

And about two quarters of an hour later…

The gates of the manor opened, and a group of martial artists rushed out, running across the land of Chengdu with outstanding Qinggong as if they were flying.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was a spacious indoor training ground.

In this spacious training ground, large enough for at least a hundred people to lie down, only one person sat quietly in the middle, surrounded by dried-up corpses, or rather, mummies.

If anyone in the world saw her, they would immediately realize what the saying ‘a beauty that could topple a nation' meant.

Beneath the hair that clung to her body, damp with sweat, was a woman who was the very embodiment of beauty itself.

Her alluring eyes were filled with lewdness, the mole on her nose was lewd, and even her plump, red, and glossy lips were incredibly lewd.

It could be said that her beauty had reached the peak of lewdness, making men angry just by breathing, causing their carnal desires to explode.

Thus, the woman sighed, a sound akin to a moan, and this human lewdness made even her sighs lewd!

And finally, she opened her mouth.

"I'm hungry……."

The unexpectedly absent-minded voice, which did not at all match her alluring appearance, suddenly shattered the mood.

The woman got up and expertly dusted off her buttocks, then walked to the wall and opened a box containing Bichuk Pills.

Only three pills remained.

But since they were covered in green and blue fuzz, it seemed like eating these Bichuk Pills, meant to remove toxins from the body by abstaining from cooked food, would actually kill her instead.

The woman frowned.

"They're spoiled……"

The woman, who had given up on the Bichuk Pills, turned her head and looked at the thick iron door of the indoor training ground.

Then, with a gurgling stomach, she seductively lowered her eyes and eventually approached the iron door, placing her hand on it.

It was a heavy iron door that was one zhang1 in height.

Surprisingly, the delicate woman displayed a powerful Inner Qi, pushing the heavy iron mass.

Creak……!

The iron door scraped against the floor, opening with difficulty.

Then, the man who had been sitting cross-legged with his eyes closed outside quietly opened his eyes.

He was a handsome man in his mid-thirties with a dignified presence, thick lines, and a square jaw that gave him a stubborn impression.

However, although he opened both eyes, one eye socket was hollow and dark. It was because he had sold one eyeball somewhere and it had disappeared.

The man covered the empty eye socket with an eyepatch and then bowed deeply as he spoke.

"You've reached the Late Stage, I see. Congratulations on your great achievement, Aunt-in-law."

"Great achievement? What's that?"

"It means you have accomplished something great."

"But I haven't reached the Unrestrained Realm yet?"

"There is no need to rush. After all, there are still countless evildoers in the world. However, your Inner Qi is not pure, so take your time."

"But I need to protect my sworn sister."

"Impatience will only lead to harm. Now, since you must be hungry, let's go and have a meal."

"Yes. Let's eat."

The woman nodded with a blank expression, contrasting with the appearance of a temptress.

Thus, as the woman took the lead and the one-eyed man followed behind…

The woman suddenly stopped and asked as if something had just occurred to her.

"By the way, is the purge over? Are there still any Eagles left?"

"Not Eagles, but Hawks. My Aunt-in-law has just taken the last of the Black Slaughtering Warlords, so the cleansing of the cult is now complete. It has been a great help. The traitors in the afterlife must be grateful that my Aunt-in-law has become their fertilizer."

"They seemed to curse a lot, though?"

"That is why I said in the afterlife. They may have been resentful when they died, but after death, they will realize in front of Yama. By giving their Inner Qi to my Aunt-in-law, wouldn't their evil deeds be slightly cleansed as a result of their virtuous merit?"

"Hmm. Is that so?"

"It is."

"If my nephew says so, then I guess it must be! I don't really know!"

The woman readily agreed.

Her naive trust was one of the few advantages of having such a pure and innocent brain.

"Hehe. Then, can I go see my sworn sister now? I miss her."

At that, the one-eyed man hesitated, stopping in his tracks.

When there was no sign of anyone following, the woman turned around and noticed the one-eyed man's somehow gloomy expression.

At that, the woman suddenly made a suggestion.

"Do you want to come too, Nephew?"

"May I, even if I am so lacking?"

"Of course, you're going to meet your stepmother as her adopted son. And I think you're already a good person? Then my sworn sister will definitely welcome you too."

Although they still had to hear her sworn sister's opinion.

However, such high-level thinking was originally impossible for a woman with such a pure and innocent brain.

Then, the one-eyed man's face lit up.

Unlike his appearance, which seemed to be over thirty, it was a very innocent, childlike smile.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Lord Kang Suyang of the Guilin Sword Sect saw the smiling faces of his disciples.

At that moment, he felt as if he had been struck hard in the head.

When was the last time he saw his disciples smile?

The Yoga Flame Room, backed by the Demonic Alliance, had been threatening them every day with their viciousness.

Even if the reason they endured such humiliations, which no martial artist should ever endure, was for the survival of the sect, the mortification felt by the disciples was surely beyond words.

But if they left the estate, where would they go?

Even if they entered another city, the sect that was already there wouldn't just stand by. And even if they managed to settle down, they would only slowly die with the dishonor of being a defeated and runaway sect.

What did they gain by enduring until it reached this state?

It was just a small hope, a vague hope that they might be able to get help from the Wulin Alliance somehow.

It was the wrong decision to make.

They should have made a decision earlier.

Even if they had to lick gallbladders and sleep on logs, they should have left the estate and planned for the future. Or, they should have attacked before the enemy could, raising the name of the sect and dying a glorious death.

Then, a desolate smile, befitting a Daoist, bloomed on Kang Suyang's face.

Fine, let's leave the estate.

Come to think of it, what is an estate and what is a business? Why should I cling to such things? As for honor, are there any who are praised throughout their entire lives? There are times in life when one becomes soiled with mud.

The founding ancestors of the Guilin Sword Sect were originally based in Guilin, but they settled in Nanning, establishing new roots.

If a sect could do it once, why not twice?

The disciples of Guilin are the Sword Sect itself, so as long as the disciples are alive and breathing with smiles like today, the Guilin Sword Sect will not die and will continue on.

The Clan Lord's decision was truly remarkable.

Because the life of a martial artist, of a sect, could be summarized in just one line.

From ancient times, losing ‘honor' meant death…!!

Of course, some might scoff, saying what honor do sword-wielding thugs have?

However, people inherently crave the most for what they lack.

Thus, the reason why martial artists, and furthermore the entire Chinese people, are particularly obsessed with honor can be easily understood.

For this reason, when Qing saw him, Lord Kang Suyang of the Guilin Sword Sect had an unexpectedly Daoist demeanor.

Since he was a part of a pseudo-Daoist sect that was almost completely secularized, it was ironic that he had such an atmosphere even though he was neither a Grand Master nor a Clan Lord.

"Thanks to you, laughter has returned to this place after a long time. I am embarrassed to have shown you such an unsightly appearance as soon as you arrived."

Kang Suyang was also embarrassed for another reason.

He had resented this incredibly admirable child for no reason, so he felt quite abashed to be so welcoming.

Of course, Qing was late.

However, traveling in Zhongyuan meant that one could not guarantee a specific arrival date.

Even if it was a month late, it was common in Zhongyuan to think that it was natural for such delays to occur on long journeys, rather than blaming the person for being late.

Thus, it was unreasonable to resent Qing for being late.

Of course, even though the mind knew this, the heart felt otherwise, so the head disciple had spoken on his behalf with complaints.

After all, wasn't it a desperate situation where the future of the sect was on the line?

In the first place, this situation was not Qing's fault. Furthermore, if Qing had arrived earlier, it might have prevented the situation from escalating, so it was actually quite a petty complaint to resent her for that.

Kang Suyang cast aside his lingering attachment and asked about his guest's well-being.

"So, are the elders in good health?"

"Ah, Lord? Before that, I have something to tell you."

"Hmm? What is it?"

"His Highness, Grand Prince Deokhyun of Sichuan, wishes to stay at the Guilin Sword Sect and is currently waiting outside. I was going to inform you of this first, so would it be alright?"

"……?"

Kang Suyang doubted his ears.

Why is a Grand Prince suddenly appearing out of nowhere?

Moreover, a Grand Prince of Sichuan of all places?

"Did I hear correctly? His Highness, the Grand Prince, has come with you?"

Qing scratched the back of her head and replied.

"Hehe, it just happened that way. If it's a burden, you can refuse."

"Why would His Highness the Grand Prince come here……?"

"Ah, we met on the way."

It was as if she had just picked up a Grand Prince on the road.

(In fact, that was what happened.)

"……?"

Suddenly, fireworks exploded in Kang Suyang's mind.

"……!"

The ultimatum was the end of this year, tomorrow.

But no matter how unruly the Demonic Alliance bastards were, they couldn't possibly attack a place where a Grand Prince was staying.

Not only could they not attack, but they also couldn't even come close with their swords. Not even loitering was allowed.

To look upon a place where a Grand Prince was staying while carrying a weapon?

Wasn't that, in itself, an act of disrespect, no different from being an assassin?

Kang Suyang, who had seemed like a Daoist, reverted to being the martial artist, Kang Suyang.

Forget leaving the estate!

This could buy them some time!

If they could just hold out until the Wulin Alliance's support arrived, they could utterly destroy those arrogant Yoga Flame Room bastards!

"Immediately, immediately we must welcome our esteemed guest. No, no, that's not the right etiquette! Where is the Grand Prince visiting? I must personally go and greet him. That is the proper courtesy, is it not?!"