\chapter{But You Said I Could Play Around? (5)}

In Zhongyuan, it was said that to see how much a host welcomes a guest, one should look at the dinner table.

And thus, Qing's eyes widened.

Since she had so thoroughly relieved their pent-up frustration as soon as she arrived, and even brought such an esteemed guest, River Lord Kang Suyak's gratitude was so immense that it wouldn't be enough even if he adopted her as his daughter and carried her around forever.

Of course, many people were aiming for that position, so it would be difficult for a mere provincial martial arts lord to obtain it, but that was how he felt, nonetheless.

Moreover, with the presence of the Prince, he couldn't afford to be negligent in his hospitality, so the table was splendid, almost to the point of breaking under the weight of the dishes, with plates stacked on top of each other due to lack of space.

"Senior Sister, this is the pride of Yangguang, soyujeo! Please try it while it's hot!"

Soyujeo was a dish of roasted suckling pig, one of the most representative dishes of Cantonese cuisine.

However, Yangguang referred to the combined regions of Guangdong and Guangxi, so it was an outrageous act to subtly include Guangdong's cuisine, the most renowned under heaven, in Yangguang, Guangxi.

Naturally, if a person from Guangdong heard this, they would be furious. Very furious indeed.

They would say, ‘How dare you barbarians who eat bugs covet Guangdong's number one cuisine under heaven?'

For reference, the people of Guangdong had the most intense pride in their cuisine in all of Zhongyuan.

So much so that it was said that if a person from Guangdong and a person from Hangzhou dined together, only one would come out alive. It was a saying that mocked the violent pride of the two regions most passionate about cuisine in Zhongyuan.

But the Guilin Sword School was in Guangxi, and its members were also from Guangxi.

Guangdong, Guangxi. They both start with the same letter anyway, and only differ by east and west, don't they?

Woo Naram skillfully sliced off the most delicious part of the soyujeo, the ribs near the front leg, and placed it on Qing's plate with a flourish.

The other side was of course offered to the Prince, so the remaining portion was entirely placed on Qing's plate.

At this, the First Disciple, Do Daljeon, twitched his eyebrow slightly.

He wondered if Naram was really a disciple of Guilin or just a lackey of the Heavenly Blossom Sword, not even offering the first portion to the Sect Leader.

But the Sect Leader had already entered the ‘Our Heavenly Blossom Sword can do whatever she wants, eat whatever she wants' state.

"Oh, Naram is really treating the guest properly! Youngest Sister, that's the most delicious part, you see."

"Wow, really? Then, should we share-"

"No, no, no. We can eat this dish whenever we have a good occasion, but it's not the same for you, right? You should eat it at a time like this."

The Guilin Sword School, being a part of the Daoist lineage, even though they were more like a secular martial arts school, was not at a level to insist on their seniority in front of a Daoist Sect Leader, but using it to pamper another's disciple was not something anyone would particularly object to.

Thus, with no one to stop him, Woo Naram was determined to pile dishes onto her plate.

"Senior Sister! This is Hong So-yu Hap!"

It was a roasted young pigeon.

In Zhongyuan, pigeon was considered a lowly ingredient for the poor, but in Guangdong, where they particularly loved pigeon meat, they raised special pigeons for consumption, which were considered high-quality.

"Senior Sister! This is Guangzhou Shao'e!"

It was roasted goose. Goose was also a friend of Guangdong.

"Senior Sister! This is Palbochae!"

Since the logistics of Zhongyuan were still underdeveloped, Palbochae made with fresh seafood was considered a top-tier luxury dish.

Of course, although it was underdeveloped, it was only in comparison to Qing's homeland. In reality, it was Zhongyuan that had the best logistics system of the era.

"Senior Sister! This is Hakka Mandu!"

These were tofu dumplings with filling inside.

In truth, if one were to discuss the essence of Guangdong cuisine, it would be the soups and congees, but unfortunately, it seemed they were not served tonight, as these types of dishes were less common at high-class banquets.

After the wave of Guangdong dishes, it was time for Guangxi cuisine.

However, the difference in presentation between Guangdong and Guangxi dishes was quite apparent.

It was understandable why the people of Guangdong would be upset when lumped together under the name Yangguang.

"Senior Sister! This is Upa!"

Upa was a semi-dried rump of a calf.

"Senior Sister! This is Pama Black Tofu!"

Pama was the name of a village, and even the people of Guangdong acknowledged the quality of Pama Mountain Tofu.

"Senior Sister! This is Aepjjangbo!"

Steamed duck feet.

"Conch! Pupa! Freshwater crab! Frog legs!"

In truth, the land was barren and the rugged mountainous terrain had not been developed much, so the food culture the barbarians ate was still strong, hence the appearance of such ingredients.

Though Qing ate well without being picky.

The First Disciple, Do Daljeon's, eyebrow twitched continuously.

He couldn't tell if that bitch was really the Second Senior Sister or just a street hawker.

Of course, every disciple knew that Woo Naram admired the Heavenly Blossom Sword as her idol.

It was obvious in the way she acted.

And she kept asking when the Heavenly Blossom Sword would come, almost as if she was eagerly waiting for a long-awaited guest.

But still, there should be a limit to everything.

She couldn't even refuse the dishes the Heavenly Blossom Sword offered and kept stuffing them into her mouth.

Even if the dishes were delicious, there was a limit. Force-feeding until the stomach was about to burst was practically torture.

Thinking about it, wasn't the person of the Heavenly Blossom Sword quite admirable for just taking it all in stride?

Of course, this was a gross underestimation of Qing.

"Mmm. Delicious, so delicious."

Qing even took off her bandages.

So, she was very excitedly stuffing her face when-

"Agh."

Qing's stomach was not an infinite bag like the treasures of some immortals in stories.

It just stretched well as she ate.

Thus, when Qing finished her meal, her upper belly would swell to an astonishing degree.

Normally, it could withstand the stomach's tyranny thanks to the sturdy bones and skin, but now one side of her ribcage was cracked, and the triple-layered muscle wall covering her side was torn.

As the stomach swelled and pushed, it put pressure on her, and the ribs, which were just starting to heal, sent a grave warning, saying, ‘Stop eating, or I'll break and burst out of your flesh.'

Qing's complexion instantly paled.

Though her serious condition couldn't be seen because she was wearing a veil, she suddenly made a pained sound and dropped her chopsticks, instantly drawing everyone's attention.

"Senior Sister!? Are you alright!?"

"No, it's just, the wound. It's fine. I can still, I can still eat more."

Qing gritted her teeth.

When would she ever encounter a table so full of regional delicacies again?

This is the time, endure it, Ximen Qing.

It was an unprecedented situation where her wound was bursting because she had eaten too much rice.

If Ximen Surin had known, she would have called her a foolish wench and said that even ghosts who died of starvation would be disgusted and run away, punishing her with Ximen Surin's special technique, the agonizingly painful Nuclear Etiquette Injection Special, the I Am Death, the Destroyer of Worlds.

"Wound? Have you been injured?"

"Yes, I got into a fight with some bandits on the way."

"What! How are you feeling?"

"It's not that serious. About a month? I should be fully recovered with about that much rest."

Usually, an injury requiring a month's rest wouldn't be considered ‘not that serious'.

But Kang Suyak had already seen Qing walking around perfectly fine, so he figured it probably wasn't that serious.

"Still. How could you get into a fight with bandits?"

"Well, I heard that Zhangjiajie was beautiful, so I was sightseeing, and they suddenly started harassing me and picking a fight, you know?"

Qing proudly recounted the tale of encountering and defeating the bandits on the road.

There were no flaws or faults in her story, as she was completely innocent. Suddenly, the bandits started picking a fight with her!

Qing, in the name of justice, could not forgive them and drew her sword, unleashing a wild storm (sword wind) and mysterious energy (Sword Qi) descended upon the earth!

As the bandits were parasites living off the blood and sweat of others, the Transcendent, Transcendently Transcendent Qing showed up. Eventually, unable to withstand Qing's overwhelming martial prowess, the bandits brought out their leader.

Thus, it was Ximen Qing vs. the Bandit Leader!

"So that Wang Cheolgun fellow was crying and begging for his life, and I said, ‘Have you ever spared another's life? Have you ever been kind to anyone even once? Don't carelessly kick away a lump of coal.' No, wait, scratch that last part. Anyway, after I said that, I cut his throat, and the rest of the bandits scattered in all directions, scared out of their minds, you know?"

It was a heavily embellished story.

But it wasn't like she could tell the truth about how she stabbed him with a poison dagger, mentioned his dead child, and kept running away until he died on his own, could she?

Her master had told her that when recounting heroic tales, one should make them as cool as possible.

Even if there was a slight twinge of conscience, it was a necessary sacrifice for a greater value.

Wasn't it her duty, as a leader and guide for female martial artists, to do great things, even if it meant being a woman?

"Indeed, Senior Sister! How impressive! Your courage to not shy away from a great enemy for the sake of justice! And your martial prowess to ultimately achieve victory! I, Woo, am truly moved!"

Woo Naram alone made a fuss.

The others were skeptical, wondering if that was really possible, and it seemed like she had exaggerated quite a bit.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since she had said she was injured fighting bandits, they called a physician, but while the patient showed no signs of pain, the physician was the one making a fuss.

‘I have seen patients my whole life, but how can a person walk around like this? Hah, truly. If it were an ordinary woman, she would be crying in pain just from breathing. It's a wonder her side isn't rotting and oozing pus. Is this a living person or a dead one? It's a miracle she's still alive.'

That's what it meant to say that she was walking around just fine with injuries that would make a physician grimace.

He thought she couldn't be so fine after dealing with the leader of the bandits, but the physician said her condition was a miracle in itself.

"What do you think?"

"It wouldn't be a lie to say that the Heavenly Blossom Sword did this, would it? Moreover, if it were a simple lie, it would be easily exposed."

The fact that the bandit leader was actually dead would soon be revealed.

If the Heavenly Blossom Sword's words were true, it would mean that the bandits who had run away in fear were not just one or two, and in time, the story would spread throughout Zhongyuan.

"Hmmm. To think that a child who just reached the Transcendent Realm this year killed a Master of the Unrestrained Realm. It's a tale I can't believe even after hearing it."

"I thought the rumors were exaggerated, but maybe they weren't."

The rumors about the Heavenly Blossom Sword were quite colorful.

It was said that she was a natural genius sent by the heavens.

At the age of twenty, she had reached the Transcendent Realm, making her the youngest Transcendent Master in the history of Wulin.

Not stopping there, she had realized the insight left by the Celestial Martial Emperor upon seeing the Absolute Sword Wall, thus grasping the meaning of the sword just by looking at the Sword Marks. A genius among geniuses.

The young Master closest to becoming the next Greatest Under the Heavens.

The successor of the Buddha's Palm, a Divine Art of Shaolin.

And her beauty was said to be that of a peerless beauty, one that could be declared the most beautiful in the world.

Anyone who heard this would laugh it off as pure lies and nonsense.

Why, they might as well say she was the reincarnation of the Yue Maiden, with the name A-Qing to boot.

Wasn't she practically the very reappearance of the Yue Maiden, whose existence was known only through stories?

"When she was still at the Peak Realm, she had already defeated the Demonic Flame Cannibal, hadn't she? Perhaps she has truly mastered a way to fight against those stronger than her."

"The gap between the Transcendent and the Unrestrained Realm cannot be explained like that. Whether what happened is possible is not really important."

"Right. We should treat that child well. I heard that the Sect Leaders of the Nine Sects One Union cherish her greatly. If she is to be the next Greatest Under the Heavens, it's only right to do so. I thought Naram was being a bit excessive, but wasn't this for the better?"

The First Disciple, Do Daljeon, frowned.

"Even so, isn't she still the Second Senior Sister? It is not right for someone who will become the next First Disciple to act so frivolously without any dignity. I was planning to give her a stern word about it."

"Just let it be since she likes it so much. Isn't a First Disciple who is a close friend of the Greatest Under the Heavens much better than a First Disciple with high dignity? It's much better for the future of our sect."

"Hmm. Isn't your leniency towards that fellow a bit excessive? It makes this current First Disciple feel a bit left out to see such blatant favoritism."

At that, the master burst into laughter.

It was the moment when the preferential treatment of Qing was decided.

It might seem too materialistic, but it was natural for the leader of a group to have such an aspect.

Of course, it wasn't just an investment for the future of Wulin. He was so grateful and it was such a commendable thing.

If she had suffered such injuries, she should have rested in a nearby city. Yet, she had hurried over with her wounded body, which was a very grateful thing.

Not only that, but she had also brought reinforcements that were akin to a thousand soldiers and ten thousand horses, which made her even more commendable.

Since the Prince had said he would stay for a month, that was enough time for the reinforcements requested from the Wulin Alliance at the beginning of the month to arrive.

Of course, if they didn't arrive within that time, he would have to desperately cling to their pants and beg them to stay, no matter what.

Since he had already seen the Prince treating the Heavenly Blossom Sword as a close friend, he could, even if it was a bit embarrassing, ask the Heavenly Blossom Sword for help.

So they had to treat her well!

They had to treat her well for the fate of the sect!

For the present and future of the sect!

Thus, the Sect Leader and the First Disciple exchanged determined glances with one mind. 