\chapter{But You Said I Could Play Around? (12)}

If there were someone with an abundance of free time who collected data on the patterns of fights between martial artists, they would find it interesting that more than half of them occurred in inns.

It was rare for fights to break out in restaurants, and in teahouses, people acted respectfully as if they had made some kind of promise.

In fact, it was only natural.

Restaurants basically had a certain price range.

Every customer who entered had a somewhat thick wallet, so carelessly starting a fight could lead to severe consequences.

And as for teahouses…

Well, those who enjoyed the leisure of a cup of tea in a teahouse wouldn't just carelessly draw their weapons, in the first place.

But inns were open to anyone.

In the Wulin way of speaking, it was a place where both dogs and cows entered.

And fights between martial artists were usually an expression of superiority.

I'm so superior, so how dare you not treat me with more respect, more special treatment?

Therefore, the anger of Hyejubiho Saheun could be considered quite justified.

I am a member of the Black-Grade Combat Unit of the Grand Under-Heaven Wulin Alliance of Evil Martial Artists!

The Grand Under-Heaven Wulin Alliance of Evil Martial Artists!

The Unorthodox Alliance for short!

So when a member of the Black-Grade Combat Unit of the Grand Under-Heaven Wulin Alliance of Evil Martial Artists told a lowly woman who sings songs to spread her legs and offered to bestow his superior seed, naturally, the lowly woman should have listened.

However, the lowly woman did not want to, so a fight broke out.

One of the characteristics of the bastards of the Evil Faction was that, except for when they had no affiliation, they rarely moved alone.

A few members of the Black Tiger Unit were enjoying a social gathering (with individual contributions) when they tried to harass a pretty traveling entertainer who, despite her lowly status, was quite the looker. But when it didn't work out, they surrounded her, brandished their weapons, and made the outrageous threat to strip her on the spot, when suddenly- Ahhh! The table made of sandalwood!

The waiter, hiding behind the waist-high counter of the enclosed kitchen, let out a sad scream.

Qing, who had been leaning against it and listening to the story, nodded.

"They're real scumbags, aren't they?"

"Exactly! The enemies of women! These womanizers should all be castrated!"

Unfortunately, when Qing entered the inn, the lowly traveling entertainer was beating the shit out of the Wulin Alliance of Evil Martial Artists' warriors like one would beat a drum.

Hmm. I thought I might see some blood for a change.

It seems like it's not going to be a bloodbath from the way she's beating them up.

Moreover, it was a fight expanded by an expert in leg techniques, which was rare.

Qing was watching with great interest and listening to the waiter's explanation of the situation.

Seniors in Jianghu often said to be careful of children, women, and the elderly.

It was advice that every senior in Jianghu gave, to the point where it felt like their ears would fall off. They would say it over and over again until you would hear it even in your dreams.

The reason was because no matter how much they emphasized it, no one ever seemed to listen.

If she was a traveling entertainer with a beautiful appearance, it meant she had the confidence to travel around Jianghu despite her looks.

However, men were apt to think with their testicles instead of their heads!

Especially since there was one head but two testicles, a one-to-two ratio, men could never defy the orders of the testicles.

And so, if you touched the wrong person, this is what would happen.

The woman grabbed the man's hair and slammed his head on the table.

Then, an Evil Faction warrior rushed in with a dagger, but with a flick, her ample skirt spread out like a flower petal.

It was a type of leg technique called Yoogun-gak, characterized by fighting while hiding the body in a wide, fluttering skirt.

"Damn it! I'll kill you!"

Finally, the Evil Faction warriors drew their swords.

Then, as the hem of her skirt fluttered, a toe peeked out and grazed the chin of an Evil Faction warrior, followed by a slicing sound.

Huh? A slicing sound?

It wasn't the sound of an impact, but a cutting sound that made Qing narrow her eyes.

Not because she was upset, but because she couldn't focus. She wanted to see more clearly.

Only then did she notice the silver glint at the tip of the woman's shoes.

She had attached blades to her shoes.

The Evil Faction warrior, clutching his neck, rolled on the floor.

Another warrior aimed for her back.

The woman spun like a top, her skirt flying out in three layers, upper, middle, and lower, completely concealing her body.

Whenever the skirt unfolded, screams of agony could be heard and people fell to the floor, clutching their wounds.

Then, one guy swung a wolf-tooth saber at the fully bloomed flower, but the fine silk just fluttered aimlessly, as the woman had already bent her body low.

And between his ankles, a powerful kick shot up! With a blade attached to the tip of her foot!

"Ugh." "Hueegh." "Well done!"

Qing and the waiter grimaced unconsciously at the gruesome sight, letting out groans.

Only Unaram, unaware of that pain, cheered loudly.

Perhaps having heard Unaram's cheer, the traveling entertainer suddenly turned this way, winked, and blew a kiss with the tip of her fingers on her lips.

It was a display of dominance so great that she flirted in the middle of a fight.

"Die!"

Out of nowhere, an Evil Faction warrior leaped up, brandishing twin willow-leaf sabers in both hands.

The decent Sword Qi contained within them drew long tails as they aimed for the back of the entertainer's head-

Thunk!!

It was a sound like a hammer striking iron.

Time seemed to rewind as the Evil Faction warrior's hands shot up again.

The paper-thin blades of the willow-leaf sabers vibrated violently, howling with a strange, high-pitched sound.

Unable to withstand the force, the Evil Faction warrior struggled to control his weapons, as if he was performing a dance that men should never do.

It was the very dance called ‘02' in Qing's hometown.

"Ah, shit."

Qing's face scrunched at the sight that was an utter eyesore.

Then, with her left hand, she picked up chopsticks one by one and threw them continuously.

The chopsticks flew, but the sound they made was as powerful as that of an iron dart.

"Ambush! There is a Ma-!"

One of the Evil Faction warriors tried to warn of such, but the tip of a chopstick, and the blade attached to it, dug deep into his temple and twisted around.

Originally, she was already a Master, but now, with the addition of Qing, who was beyond Transcendent, continuously throwing chopsticks, things were different.

"I'll help too!"

Unaram joined in, drawing his soft sword and spraying Sword Qi everywhere.

With the Black-Grade Combat Unit, the middle rank of the Black-White-Yellow, now missing its leader and deputy leader, and just a bunch of guys having a social gathering, how long could they last?

The last Evil Faction warrior collapsed.

He would have looked more dignified if he had fought bravely, but he had died a pathetic death, with a chopstick protruding from the back of his neck after showing his back and trying to run away.

Then, the traveling entertainer approached Qing and offered a greeting.

She crossed her palms in a straight line, covered her mouth, tilted her head slightly downward, and bent her knees in a gesture of respect called Sukbae, which was the second most polite greeting a woman could give.

For reference, the highest form, Cheoneuprye, could only be performed towards the Emperor, one's teacher, parents, and towards the heavens during ancestral rites. As such, it could be said that she was showing the most polite form of greeting practically possible.

"I am Nayanggyeol of the Hall of a Thousand Flowers. I offer my deepest respects to the Senior Martial Artist of the female sect. If it is not too impolite, may I inquire as to your esteemed name?"

Qing realized the woman's misunderstanding.

Throwing chopsticks to block a strike imbued with Sword Qi, and even making a man dance a hideous dance with the residual force… She must have thought Qing was a profound Master of a female sect.

And usually, female Masters tended to be somewhat older, so seeing Qing's veil, she must have assumed she was some great senior of Jianghu.

"There is no need to be so stiff and formal. I am Ximen Qing of the Divine Maiden Sect."

"Ximen Qing? The Heavenly Flower Sword?"

"Although I am inadequate, that is what I am called."

For some reason, the woman's expression turned sour.

"Hmm. The Heavenly Flower Sword, you say. Well then, shall we move to another place? Actually, I came here to meet you."

----

The Hall of a Thousand Flowers, or Cheonhwajeondang, meant a manor of a thousand flowers.

It was a mysterious sect composed solely of women.

For reference, in terms of fame, the Emei Sect ranked first, the Hall of a Thousand Flowers second, and the Divine Maiden Sect only third.

After moving to a room, Nayanggyeol let out a deep sigh.

"Actually, the reason I came to Namnyeong was to meet the Heavenly Flower Sword."

"Me?"

Nayanggyeol hesitated for a moment before speaking.

"In our Hall of a Thousand Flowers, we have long called our head disciple the Heavenly Flower (天花). The Great Senior of this generation is called the Earthly Flower and the Great Senior of the third generation is called the Human Flower."

"Hmm. And?"

"Although the shapes are different, strictly speaking, flower (花) and brilliance (華) are the same character, are they not? So, the title Heavenly Flower Sword that you are using has become quite a difficult matter for our Hall of a Thousand Flowers. Moreover, the name of our sect is the Hall of a Thousand Flowers, so while I know that the Heavenly Flower Sword is not a title you chose for yourself, I'm sure you understand what I'm trying to say."

"Ah."

Qing made a sound of realization.

It was indeed a problem.

If there was a female Master whose title was Divine Maiden Sword or Temptress Sword or Temptress Divine Maiden, what would become of the Divine Maiden Sect, which worshipped the Temptress?

If there was a Hwasan Demonic Sword unrelated to Mount Hua, a Wudang Wind Sword unrelated to Wudang, or some swordsman called themselves the Shaolin Divine Sword, everyone would be in a difficult position.

Of course, no one would dare touch the Nine Great Sects.

However, among female martial artists, there were occasionally Divine Maidens who were not part of the Divine Maiden Sect, so it could be said that the less famous and less powerful sect was at fault.

"I guess I should change my title. But how do I go about changing a title……"

At that, Nayanggyeol shook her head.

"Before that, may I check your face?"

"Yes?"

"The Mistress said that I should check if you are qualified to use the title of Heavenly Flower. If the title of the Most Beautiful Flower Under Heaven, the most beautiful flower among flowers, is true, then our sect will gladly send our praises to the most beautiful person of this generation."

"Isn't that! A bit too much!!"

Unaram, who had been listening, suddenly shouted.

The expression ‘gladly send our praises' was just a roundabout way of saying that if the Heavenly Flower Sword wasn't the most beautiful person under the heavens, they couldn't acknowledge the title and she would have to change it.

But who in the world decides who is the most beautiful person under the heavens?

The Han people might think a big chest is a symbol of stupidity, lewdness, and evil (though they wouldn't say no to it), but for the Zhang people, the size of a woman's chest is the most important element of her beauty.

Even just looking at the Five Beauties of Wulin, there were surprisingly many who preferred a fierce impression with dirty glares like Hyeonhwa, or those who liked the calm and sickly beauty like Seolhwa, as Qing did.

Or the (seemingly) gentle cuteness of Dokhwa, or the bold cuteness of Geomhwa, each with their own following, differing in tastes.

Then there was also Paekhap, the traditional beauty without any distinct features.

Since the standard of beauty wasn't something that could be quantified into a score, how could the Hall of a Thousand Flowers decide whether to acknowledge it or not?

So, even though they said ‘acknowledge' or whatever, it was basically just telling her to change it.

This was exactly why Unaram was so indignant.

"Hey, Naram-ah. But the people from the Hall of a Thousand Flowers have a point. If my title was something like, say, Gyelim Sword Empress, how difficult would that be for the Gyerim Sword Sect?"

"Hmm…… Indeed! Big Sister! This Unaram! I am full of admiration, once again! I am moved, once again! I am in awe, once again! True Great Heroes are those with such a broad mind! A wide chest! A vast chest! A magnificent chest! That huge chest has room enough to embrace all under heaven! Such a Great Hero, indeed!!"

Hmm. I understand that you don't have any malicious intent.

Still, it's always chest, chest, chest with this guy.

Not that she's coveting it like Nanah, but, hmm, Nanah, I kinda miss her a bit now.

Should I stop by Sichuan on my way back home?

"I am grateful that you understand. Honestly, even I found it difficult to bring this up, and as for the issue of the title, we will discuss it with the Wulin Alliance so-"

Nayanggyeol, who had been pouring out words of apology as if unable to hide her sorry heart, suddenly stopped speaking.

And her expression was as if she was in a daze, or drunk, or had just witnessed an unbelievable sight with her own two eyes.

It was the side effect of beholding Qing's beauty, who had removed her veil just in case.

"Miss Na?"

At that, Nayanggyeol snapped back to attention and nodded with a serious expression.

"As the one entrusted with full authority by the Mistress, our Hall of a Thousand Flowers acknowledges your right to be called the Most Beautiful Flower Under Heaven. Indeed, the greatest under heaven is also the greatest in her insight, as well as appearance. If Young Lady Ximen is not the Heavenly Flower, then what flower in the world could be called the Heavenly Flower?"

"Eh?"

What? The incident was suddenly resolved?

As Qing blinked in confusion, Nayanggyeol looked directly at her with a determined expression.

"Young Lady Ximen, however, I have another favor to ask. Please do not misunderstand and hear me out."

"What is it?"

At that, Nayanggyeol answered.

"Please become my partner. I have fallen in love with you." 