\chapter{But You Said I Could Play Around? (4)}

"Y-Y-You, you retarded son of a…!"

Gu Hwanjeol, the current leader of the Great South Ningyo Clan, formerly known as the Yeom-Bang, raised his fist.

"Eek."

At that, his third son, Yo Min, who had been disowned, raised his arms to cover his face.

Judging from Yo Min's immediate reaction, one could tell that Gu Hwanjeol had often struck him in the face with his fists.

However, whether he covered it or not, it wouldn't really matter. After all, his face was already swollen on both sides, bruised black and blue.

"You piece of trash, you worthless bastard, you retarded, incompetent, moronic son of a bitch."

But Gu Hwanjeol could not bring himself to punch.

It wasn't because he could never acknowledge him as his son, but rather because his cheeks were already so dark that it seemed like they were on the verge of necrosis. If he hit him now, he might actually end up having to hold a funeral.

There was no benefit to having a rumor spread that he had beaten his son to death.

He was a useless son anyway, so he should use him frugally and discard him. After all, wasn't beating him to death in anger just a loss?

Gu Hwanjeol was the very embodiment of the Salt Gang, filled to the core with a salty disposition.

But more than that, he was just dumbfounded.

How in the world can one get beaten to the point where they end up looking like this?

Even if you were hit hard in the jaw, it might swell up, but to think the wound would be so severe that it would turn black… Was the assailant's hand covered in poison or something?

Well, he did get hit in the face with the White Hand Demonic Arts.

The extremely venomous poison of the White Hand Demonic Arts, which was the very essence of a woman's spite, would destroy the blood and energy vessels upon permeation.

And it didn't just destroy them, but froze them as if frost had fallen, before shattering them into pieces.

"You, ha, fine, whatever. I shouldn't have expected anything from a bastard like you. I don't even want to look at you, so get lost. Now."

Gu Hwanjeol waved his hand in disgust.

He wondered what kind of idiot would come out of his loins.

If only he had shown any talent for martial arts.

Or maybe he could have been good at business, thus earning some money.

But his body was so laughably weak that he would never reach the First-Rate Realm in his entire life, let alone master martial arts.

And on top of that, he was so foolish that his thoughts were shallow. Yet, he only knew how to squander money, becoming a parasite that only knew how to eat away at the family's fortune.

He didn't even want to think about having such a bastard as a son.

Every time he saw him, his blood would boil in rage.

"Yes……."

Yo Min answered in a tearful voice.

Of course he would cry.

What had he done wrong?

He had gone every day as he was told, to harass them. And he had expected to get beaten up badly at some point.

Of course, being forced to lick the ground in front of everyone was so humiliating that he wanted to die. But he couldn't just abandon his life because of that, could he?

That was what his father wanted, but Yo Min couldn't even fathom that his father would send him out to die, no matter how much he hated him.

So he was sad.

If he had to compare, his eldest brother was also terrible at using his body, so wasn't it a case of ‘same difference', ‘six in one, half a dozen in the other', and ‘pot calling the kettle black'?

In the end, it was all because of his mother, who had run away from home after falling in love with a ronin.

So he was just angry.

Angry at his uncaring father, angry at his mother who abandoned her child and left on her own, and angry at the martial artists and servants of the Salt Gang who mistreated the abandoned child.

Both his cheeks burned, but hotter tears flowed over them.

He was sick and tired of everything, so he headed for the medicine hall.

But that was when it happened.

"Hey, you. The third son, was it?"

Yo Min hurriedly wiped away his tears.

But it was already too late.

"Why is a grown man sniffling like a child? Tsk tsk. No wonder you're out of your father's favor."

Yo Min flinched.

But what could he do about it?

After all, his interlocutor was a physician who used the character ‘sa' (蛇), meaning snake, as well as an expert in poison.

He was known as the head of the medicine hall, a high-ranking expert who had mastered the Heavenly Snake Poison, Boyeol of the Four Snakes.

"But, you… Why is your face like that? Did Lord Gu really have such a harsh hand? No, no matter how upset he was, how could he hit his own child like this? Hm? No? This isn't it? What is this?"

Boyeol approached, grabbed Yo Min's chin, turned it left and right, and then raised his left hand, revealing a snake that suddenly emerged from his sleeve, flicking its tongue.

"H-Hiiiek."

Yo Min froze in fear.

He couldn't even breathe. If he was left like this a little longer, he would probably piss himself.

"There's no need to be so scared. I was just trying to examine your wound."

"Y-Yes. But this snake……."

"Don't worry about it. Even if you get bitten, there's an antidote, so there's no need to worry."

That didn't sound reassuring at all.

Saying there was an antidote if he got bitten meant that he might get bitten, didn't it?

With its red eyes, the sharp triangular head of the white snake was clearly that of a venomous snake.

The venomous snake carefully approached, sticking out its head, until it suddenly made a hissing sound and retreated back into his sleeve.

Yo Min's moment of relief was short-lived, as Boyeol asked with a serious expression.

"You, who hit you? It couldn't have been Lord Gu, right?"

"Th-That, the Heavenly Flower Sword, some bitch called the Heavenly Flower Sword……"

"Heavenly Flower Sword? The Divine Dragon? Are you talking about the girl who won the Hidden Dragon Latent Phoenix Tournament? No, that can't be, right?"

"It's true. There were many witnesses."

Yo Min couldn't continue.

It was too humiliating to put into words.

At that, Boyeol's eyes flashed.

"I see, so that's how it is……."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing did not know just how high the status of the Imperial Family was in Zhongyuan.

This was because she was someone who came from a place that didn't even have a king. In fact, even when looking at the entire world, monarchs only really existed in a symbolic form.

Of course, even on Qing's homeworld, Zhongyuan was a theocratic imperial society.

It was an empire where an iron man with the fearsome title of Chairman, a combination of emperor and cult leader, ruled over a billion people all by himself.

However, since Qing wasn't a Chinese at the time, she had no way of knowing the power of the Chinese Emperor.

So Qing did not understand the natural difference in status, nor the existential fear that if one defied them, a million-strong army would pour down like a rain of arrows and cannon fire.

So even when she heard she was a princess, she didn't think much of it.

However, she did see how Gang Suyang, the leader of the Gulin Sword School, knelt down and welcomed freedom.

So Qing thought that it felt a little real.

Of course, Gang Suyang was just being dramatic.

It was a good look to have the leader of the city's top sect personally greet a prince, and it was a story that could be considered a form of local legend.

So there was no reason for Gang Suyang to refuse.

As such, it was inevitable that Qing's needs would be pushed down in the list of priorities.

After receiving the guest room and unpacking her luggage, it was already late afternoon and she had nothing to do.

Originally, there should have been a schedule where she would drink tea with the sect leader, receive his warm words, and be introduced to the disciples, but what could she do when the prince had come to visit?

Thus, Qing was left to do nothing.

Well, whatever. Fine by me.

Thinking that it was nice not to have people bothering her since the prince was around, Qing laid down on the bed and lazed around.

But then…

-Excuse me, Heavenly Flower Sword Senior? Are you inside?

"Ah. Yes."

-My name is Woo Naram, a Second-Class Disciple. If it's not too much trouble, I would like to, like to pay my respects. Would that be alright?

"Trouble? Not at all. Come on in."

Then, the door opened with a creak and Woo Naram entered the room.

Wow! Brown skin! A healthy beauty! A fitness girl!

She was a beauty with a beautifully tanned, brown skin, something that would have cost money to achieve back in Qing's hometown. Um, wait, is she a beauty?

Although her eyesight had improved a lot, people still appeared to be scattered into six.

Still, it was much better than before, when dozens of afterimages lingered.

Woo Naram carefully entered the room, then stood at attention and performed a formal fist and palm salute before shouting.

"G-Greetings! I am Second-Class Disciple, Woo Naram! Although I am ashamed, I hold the position of Eldest Senior Sister!"

Her voice was truly loud.

"I'm Ximen Qing. Nice to meet you. And my ears are fine, so there's no need to shout like that."

"The, the honor! The honor is mine!"

Woo Naram's eyes were sparkling, a gaze that would have been quite burdensome if Qing had known what it meant.

"There's no need for such formalities-"

"No! Senior has such a beautiful appearance, is incredibly powerful, possesses great elegance, and is also a disciple of the Zenith Among Women! Moreover, you have an outstanding ability to drink and are generous! On top of that, you are also considerate of others, so are you not a true heroine!"

"Ah, were you at the Hidden Dragon Latent Phoenix Tournament? Why didn't you say hello?"

"Not just the Hidden Dragon Latent Phoenix Tournament! I have watched every moment Senior has taken to the stage! The divine realm where you overwhelmed those boastful men with a single strike! Th-That move during the finals, I heard it was called Kaleidoscope, a technique you realized from the Insight left by the Celestial Martial Emperor. The beautiful rain of Sword Force that filled the entire world is still vivid in my eyes! And then before that, when you fought against Monk Wolbong of Shaolin, it wasn't gentle but powerful! It was truly……"

Woo Naram's words poured out, recounting each of Qing's matches in reverse order. It seemed like she had recounted them many times before, vividly describing each and every move.

"……Thus, this Woo Naram wants to emulate Senior! You are truly the star of female martial artists, no, a shining sun! This one has longed for the day I would meet Senior, waiting a day as if it were a year! And like this! Finally! To meet Senior, my heart is pounding so much! This emotion!! I cannot possibly express it with mere words!!!"

It seemed like she wanted to express this emotion that could not be put into words through the sheer volume of her voice, which had gradually increased until it was practically a shout.

"Uh, calm down for a moment……"

"Senior! Therefore, this insignificant Woo Naram of Jianghu has a lifelong wish! I humbly wish to serve Senior, so may I dare to call you Older Sister!?"

The title Older Sister was also used between women.

Just as a younger brother could become an older brother, a younger sister could also become an older sister.

Of course, that was just in words, and it wasn't a commonly used term.

At that, Qing's expression became a bit subtle.

"Well, Miss Woo? If I may be so presumptuous, how old are you……"

If she was the Eldest Senior Sister, she would have to be at least in her mid-twenties, no matter how young she looked.

Even if the disciples had recently changed generations because the sect leader had a young appearance, it was still the same.

"This Woo Naram will be thirty the day after tomorrow, with the passing of the new year! However! Originally, age does not matter at all when serving an Older Sister! What is important is respect! Character! Skill! How can I express this respect I have for the Senior I admire with anything other than Older Sister!! That is what my heart wishes to shout!!!"

Qing thought to herself.

What? Age doesn't matter? It should.

But Qing understood.

It was the same principle as when younger fans of a younger idol called them Oppa.

Of course, Woo Naram being almost thirty didn't really matter to Qing.

Whether someone was older or younger, Qing would just speak casually as she saw fit.

"Just call me Qing. Miss Woo? Is that right? Not Miss Woona, right?"

"If that is what Senior wishes, I shall be Miss Woona. And how could I dare to lightly speak Senior's esteemed name……."

"Don't do that. Let's just speak casually to each other, okay? How about it? Naram-ah?"

"I-It is an, an honor!"

"Hey, speak casually, remember? Friends? We're friends now? Starting from today, it's day one? Drop the family name and the title. Qing is Qing and Naram is Naram, okay? Agree? Do you agree?"

It was a friendship declaration that flowed as smoothly as water.

However, Naram did not flow along.

"I-I cannot do that! Senior is my idol! My ideal! How could a firefly and the sun be on equal footing!! This one can only serve you as an Older Sister. It would be my lifelong wish, the honor of three lifetimes!"

Qing thought for a moment.

Is Older Sister better than Senior?

What's with all this Senior, Senior stuff? It's burdensome.

"Then, can you call me Young Lady Ximen or Young Expert Ximen……?"

"How could I possibly express my burning respect with just that!"

"……?"

Shouldn't respect that is on fire be put out?

Wouldn't it just turn to ashes later?

Qing carefully asked again.

"W-we're not going to be sworn sisters, right?"

Once before, she had been tricked by the cunning Gyeonpohui and ended up with an older sister.

She asked if they could use the same family name, and suddenly she was calling her Older Sister, so it just happened somehow.

"How could I dare! Such an outrageous, and insolent, and presumptuous, and impertinent thought has never once crossed my mind!"

"No, it's not that big of a deal……. If you really want to, it can't be helped."

Well, if she wants to that much, then whatever.
