\chapter{But You Said I Could Play Around? (8)}

Qing checked the shape of the moon outside.

Let's see, what time is it now? It should be around the end of the Rat Hour or the beginning of the Ox Hour1?

It's not that Qing's estimate was just a rough guess.

It was because calculating time by observing the celestial bodies didn't provide an exact time.

It had already been half an hour since the appointed time, which was midnight.

However, since Qing was alone, it wasn't because she overslept and was late to the appointment.

After all, she had arrived at the meeting place very early.

The Dragon King Room of the Dragon Palace Inn.

Just from the name alone, it was the best room of the Dragon Palace Inn.

And the Plum Blossom Room was right below the seventh-floor Dragon King Room.

Qing had been focusing on the sounds coming from there with her ears perked for nearly an hour.

But there were no unusual findings.

Other than the muttering of someone wondering why the other wasn't coming when it was already past the appointed time, whether the letter had not been delivered, or whether it had been received and ignored.

After carefully listening for about half an hour more, Qing concluded that there were no companions present.

It was only then that Qing opened the door leading outside.

The reason why it was a door and not a window was that in such high-end rooms of tall buildings, the walls were made entirely of sliding doors.

Qing lightly jumped onto the eaves of the lower floor.

Her waist screamed in pain, but she could bear this much now.

Suppressing a groan, Qing knocked roughly on the door, putting the resentment she felt towards her waist into it.

Then, with the sound of approaching footsteps, the door opened.

"Hehe, I didn't expect you to come from the window. Come in, come in."

Isn't this person not hostile at all?

Qing felt a bit relieved.

The owner of the letter was an old man with wrinkled skin.

His skin was covered with age spots and the parts that weren't were shiny and oily in that way only old people's skin could be. With his deeply set wrinkles, he seemed to be at least a hundred years old.

"So, you know my secret?"

"My, how impatient. You have made a person wait for half an hour, yet you immediately start with your own business. That's not right. My name is Bo Yeol."

"I'm Ximen Qing of the Heavenly Flower Sword."

"Yes. Do you enjoy the Dao of Tea? Since you have come to Guangxi, you should drink Liubao."

Liubao tea was one of the renowned teas under the heavens, practically the only specialty of Guangxi Province.

Naturally, as it was a treat for honored guests, the Guilin Sword School had served it to her endlessly.

"I've already had enough of it. I've even had it as chongshi tea. Do you have any Longjing tea by any chance? The medicinal scent of Liubao tea is too strong for my taste."

Chongshi tea referred to tea made from the excrement of caterpillars that had eaten tea leaves.

It was not only expensive but also incredibly rare.

At that, Bo Yeol's expression turned sour.

"The Guilin Sword School served you chongshi tea?"

"Yes."

"Ha, those stingy bastards. To think they would treat even a young child with chongshi tea. Tsk. Forget it. Just drink this. It's not like I can call someone to change the tea leaves at this hour, and you wouldn't want to show your face to others, would you?"

Then, he busily mixed water, using several teapots to adjust the water temperature on the brazier.

As he poured the tea, he grumbled.

"Longjing, you say. Those who don't know tea always look for Longjing. Because they don't know any tea besides Longjing. What's so great about Longjing anyway?"

It was suddenly a tea ceremony atmosphere.

Qing just blinked, then turned her gaze to the sweets neatly stacked like gold ingots on the table.

They were translucent, yellowish, rectangular sweets with something that looked like a yellow peel embedded in them.

What is this?

It looks too suspicious. Far too suspicious.

Since it's suspicious, I should try it. Nom, nom.

The sweet was made from candied kumquats, a type of kumquat confiture.

However, compared to confiture, it had a chewy texture with a lot of kumquat filling. Ah, this is…

Wow! It's sour and sweet!

After tasting the flavors of her homeland for the first time in a while, Qing's expression brightened.

"Why are you only eating the refreshments when the tea leaves haven't even steeped yet?"

"Um. Yes."

It's not like this is the time to eat and play around.

Qing looked dejected and put down the sweets.

Thus, the room was filled with the medicinal scent unique to aged tea (in a good way).

"It is done."

Originally, in Zhongyuan, tea etiquette was separately classified as the Dao of Tea.

The reason why the old man said ‘It is done' after brewing the tea well was that it was originally the role of the younger person to serve tea to the elder.

Of course, usually, the host would serve the guest first, but the two of them were not in a host-guest relationship.

Qing's tea ceremony skills were honed by the rigorous nuclear bombardment of Ximen Surin.

With an elegant motion that would impress even a skilled tea master, she brewed a cup of tea, to which Bo Yeol expressed his gratitude by tapping the table three times with his fingers, a custom of southern China.

Qing first took a deep breath to savor the aroma, then lightly moistened her lips to taste it.

Hmm. It's tasty. But there's this ginseng smell…….

The unique feature of Liubao tea was its ginseng-like scent.

"So, you said you know my secret, Elder?"

"Hmph. You are indeed impatient."

"It's late at night, so what is the use of being patient?"

"Hehe, that's not wrong either. Well. If it were anyone else, they might not know, but there is no way I would not know."

At this, Qing looked at Bo Yeol with a nervous expression.

My secret? Just what does he know?

"You are the Minor Demonic Arts' Successor of this generation."

"Huh?"

"Hehe, it is quite a masterpiece. To think the Minor Demonic Arts' Successor would be the identity of the Divine Dragon, the most outstanding among the Orthodox Faction's Rising Stars. Who could have imagined it?"

Bo Yeol laughed as if he found it very amusing.

Qing asked cautiously, a bit disappointed.

"Uh. Is that all you know about my secret? That I learned the Minor Demonic Arts?"

Wait. Is that it? You knew I learned the Minor Demonic Arts?

The middle of the night, in the most expensive room… You kept me from sleeping and made me stick my ear to the floor for an hour, listening carefully for any suspicious signs, just for this?

Wait. No way, right?

"Is that all?"

Qing felt both relief and caution at the same time.

That's right. Get to the main point, old man!

"How many people do you think know that the previous, or should I say, the current Minor Demonic Arts' Successor, since you're here, was affiliated with the Blood Cult? As the one who inherited the Minor Demonic Arts, you are practically a Demonic Human of the Blood Cult, are you not?"

"Uh, and?"

"You have deceived the people of the world quite thoroughly. Even I could not imagine such an identity."

Ah, shit. It's a bust.

Qing was disappointed again.

In fact, she didn't come here with only caution because he said he knew her secret.

She had hoped it might be related to the status window, or perhaps another person who had crossed over from a different era.

She thought she might be able to ask for help from someone with more information than her, or at the very least, they could have had a friendly chat, talking about ‘the top 100 reasons why Zhongyuan are uncivilized' or ‘sharing stories about making modern food'.

But what? Just because I know the Minor Demonic Arts? He made me come all the way here at this late hour, just for that?

This is a complete loss. No, it's my complete loss. A loss of half my life.

Ah shit, my expectations, my vigilance, my money, my time, and my effort. Give it back.

To compensate for her losses, she decided to indulge in the expensive sweets.

Qing's outrageous act of munching on the kumquat confiture, a snack that should be paired with tea, was a form of retaliation against Bo Yeol.

It was similar to eating snacks in front of a drinker without offering any, an act that could be considered inhuman and utterly atrocious.

Despite Qing's terrifying retaliation, Bo Yeol just chuckled.

"There's no need to be so anxious. I didn't call you here to say such bad things."

"Ha. You're just saying that because you found out. In truth, my real identity isn't Ximen Qing."

"Oh? The Wulin Alliance is truly full of spectacles. A while ago, it was the Murim Alliance's patroller, that Un kid, who turned out to be a spy for the Blood Cult. And this time, it's the Divine Dragon. So, what is your real identity?"

Ah, so you know Un Yeonyoung.

Qing had been enjoying impersonating Un Yeonyoung lately.

She was about to do it again, but was preempted.

"It's a secret. I won't tell you. Figure it out yourself if you can. So, why did you call me here? If you don't want your identity revealed, you better listen to me quietly?"

"Well, something like that."

"You're calling the Minor Demonic Arts' Successor here just like that? Aren't you scared? Want to taste the Minor Demonic Arts?"

"I left a letter in my room. If I don't return, someone will come looking for me, and they'll find the letter with your identity. Then the whole world will know your true identity. If you're fine with that, then so be it."

"Wow, that's a really scary threat."

Her Master had already taught her that she could just deny everything, so Qing wasn't afraid at all.

However, she was curious after hearing what he said.

What does he want me to do that he prepared such nice tea and delicious snacks?

I listened for an hour, sticking my ear to the floor, and concluded that this old man came alone without any companions.

"So, what do you want?"

Qing, who could not contain her curiosity, asked.

If he said something obvious like ‘take it off' or ‘let's enjoy the cloud and rain', she was going to send him to the afterlife with a special combination of the Ten Great Demonic Arts: Minor Demonic Arts + Black Killing Demonic Palm + Purple Lightning Demonic Arts + Wheel of Samsara Demonic Tribulation.

Unfortunately, the One Hundred And Eight Asura Sword can't join because people only have two hands.

Wait. What if I held the sword in my mouth like that one guy? Then, could I use half a set of the Ten Great Demonic Arts?

Unfortunately, the old man seemed to lack the vigor of his youth.

Bo Yeol took out a small medicine bottle from his bosom.

"Now, this is called Blood Fiend Poison."

"You want me to drink this? And if I want the antidote, I have to obey you?"

"You're a Demonic Human of the Blood Cult, yet you're ignorant about poisons. How can you not know of Blood Fiend Poison, one of the Ten Great Poisons Under Heaven?"

At that, Qing tilted her head.

"Another Ten Greats? Seriously, who decides these top ten lists? Moreover, who decides which ten poisons are the strongest? Did someone go around tasting every poison in the world and rank them based on how painful and potent they are?"

"Ahem. Hmm, hmm."

In fact, apart from a few truly famous deadly poisons, the rest were just a list filled with well-known poisons.

An important aspect was that poison masters would sneak in poisons they had made.

Since Bo Yeol had also sneaked in a deadly poison he had made into the list of Ten Great Poisons Under Heaven, he cleared his throat awkwardly, repeatedly taking sips of his tea.

Then, he reached out to cleanse his bitter tongue with some refreshments, only to pause and stop his movements.

Why, oh why, were there no refreshments left?!

Now, Bo Yeol had lost his means to cleanse his bitter tongue.

He would have to continue suffering, which was the terrifying revenge of Qing's thoughtless munching.

"So, what do you want me to do with this?"

"Feed it to the leader of the Guilin Sword School, Gang Suyang. It won't be bad for you either, right? I won't question what the Blood Cult is plotting, but wouldn't the disappearance of an Orthodox Faction be something you would also welcome?"

That was Bo Yeol's scheme.

Since the Blood Fiend Poison was practically Sasa's signature move, if Gang Suyang died from poisoning, it would soon be revealed that Bo Yeol was behind it.

Then, it would be as if he had single-handedly accomplished the mission of taking over Guangxi, thus allowing him to monopolize all the credit.

Qing pouted.

He seemed friendly, but it turns out he was just another member of the Unorthodox Faction.

However, Qing fell into a dilemma.

Because she was very tempted by the poison.

I want it! One of the Ten Great Poisons Under Heaven!

Qing had already poisoned two Unrestrained Realm Masters to death.

She didn't know if it was really one of the top ten poisons in the world or just the maker's exaggeration, but it was certain that it was an incredibly powerful deadly poison.

With this, I could easily kill an Unrestrained Realm Great Demonic Adept, right?

It was a righteous idea from one of the greatest Rising Stars of the Orthodox Faction, wanting to eliminate a Great Demonic Adept.

"So, you want me to kill Gang Suyang with this poison. Then you'll overlook the fact that I'm the Minor Demonic Arts' Successor?"

"Exactly."

"Hmm. Understood."

Qing said as she snatched the poison bottle.

Woohoo, got a deadly poison.

However, Qing only said she understood, not that she would do it.

One could say that she was a wicked person by nature, shamelessly deceiving and scamming an old man without even batting an eye.

"Indeed. It's nice when things go smoothly. Don't think of it as a threat. Isn't this good for both of us?"

Bo Yeol, completely unaware that he had been tricked, smiled, his old face blooming with wrinkles. 