\chapter{But You Said I Could Play Around? (1)}

When the soldiers set the fire, the geomancers predicted that a southeasterly wind might blow.

Although they tried to cover as wide an area as possible to avoid responsibility, weather forecasting was a science that relied on statistics from the past, present, and even the future.

Therefore, the geomancers' opinions were also based on a large amount of data that showed that southeasterly winds blew in this area around this time of year.

Even the great Zhuge Liang of the past, in a situation where everyone would die if the wind didn't blow, calmly pretended to be a shaman and said, ‘The wind will come. It will come'.

According to later analyses, the area of Red Cliffs at that time was a place where northwesterly winds originally blew strongly, followed by a high probability of southeasterly winds afterward.

It is said that he gained confidence by observing a few weather signs, such as distant rain clouds in the south, low-flying insects, and unusually active fish.

So if Zhuge Liang had been there instead of the geomancers, he would have confidently said, ‘Don't worry and set the fire. I will borrow some rain clouds and make it rain around tomorrow,' showing off his skills.

For this reason, Qing was awakened by cheers that erupted unexpectedly early in the morning.

It was like the cheers one might hear when their country scored a goal in an international match.

(Although such a thing could never happen)

So, wondering what was going on, she opened the window and looked outside to see heavy rain pouring down in early winter.

Scientifically, it was a natural occurrence.

Because the summer was too hot.

As a result, even in winter, the South Sea had not yet cooled down, causing large rain clouds to form.

So the rain clouds, riding the southeasterly wind, were covered in the black smoke뿜뿜ing from the fire, the hot smoke filled with ashes, and immediately began to shed tears because their eyes stung.

But Qing did not know this.

The primitive people of Zhongyuan also had no way of knowing this natural principle.

Therefore, they were simply cheering and expressing their gratitude for the heavy rain that would extinguish the fire.

Thank you, Buddha! Thank you, Lord Above!

And since the heavens had stopped a disaster on earth, it must be because the Son of Heaven was virtuous!

Thus, from early dawn, people in the streets were shouting ‘Long live' while being rained on.

Long live the Emperor! Long live! Long live!

Long live! Long live! Long, long live!

May you live a long life, oh Emperor!

Emperor! May you live ten thousand years in good health!

Originally, all good things were solely due to the virtue and grace of the Emperor.

On the other hand, if something bad happened, it was all the fault of the people, and if the people needed to be appeased, it was because an evil woman had entered the imperial family. So one could just blame it all on women.

Hearing that, Qing snorted.

Long live, my ass.

The one who told them to set the fire in the first place was that very same guy.

But, what kind of person was he really?

It was a thought she had been avoiding, not wanting to think about it.

If Empress Jin was right, he would probably be her biological father.

Based on what Qing had seen, heard, and experienced in Jianghu, it was clear that he was definitely not a decent human being.

The way Empress Jin gritted her teeth was full of a woman's resentment, and she had also treated Imperial Concubine Yeon very harshly.

Apart from that, the state of the country was a mess.

She knew that the people were treated worse than dogs or pigs.

At least dogs and pigs were raised and not caught unless there was a need, were they not?

If they went as far as to kill people and set fires while pretending to be bandits just to silence them…

But, um. What does that have to do with me?

After all, Qing was just Qing.

There was no reason for her to raise the banner of rebellion, claiming she would punish the immoral emperor, or to write the four letters of democracy in blood, shouting, ‘Our lives are solely for the revolution! Sign here, comrade! The Red Ideology is the only specter haunting the world!', while passing around a solemn petition.

Why would Ximen Qing, a martial artist of Jianghu, get involved in the affairs of the high and mighty ruling the country?

Ziyou also opened the window and looked outside.

She watched the pitiful people who were rejoicing and dancing in the winter rain, repeatedly raising their arms and shouting ‘Long live'.

Did they know that it was the heavens that sent down this fire?

But what difference would it make even if they knew?

To them, the Son of Heaven was the heavens.

People could resent the heavens, but in the end, they could not escape from it. So when they were driven to the edge of a cliff, they could only pray to the heavens.

That was why all the sages discussed the proper way for a ruler to govern.

Since an unkind heaven merely burns the world by striking it with lightning, leaving only tears and despair overflowing on the earth.

Then, should those poor people just beg for mercy and live on as the heavens become violent?

‘But isn't he doing a good job, as a result?'

Suddenly, Qing's words came to mind.

He had never thought of ascending to the Dragon Throne.

Although he had governed Sichuan with benevolence, it was merely a desperate act to avoid being noticed. He had never intended to improve the lives of those people.

But they… those foolish and pitiful people who thanked the heavens for trying to kill them.

Suddenly, there was a flash, and the entire world lit up for a moment.

Rumble……!

A beat later, the sound of thunder echoed through the world, but Ziyou's face was already shadowed once again.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Guilin Sword School of Nanning Prefecture, Guangxi Province.

Honestly, if one were to hear the name Guilin Sword School of Nanning Prefecture, it would likely elicit a chuckle.

This was because there was a city called Guilin in Guangxi Province.

Guilin, famous for its lush growth of cassia trees and considered one of the most beautiful cities in Zhongyuan, was also one of the oldest cities in the southern part of the Central Plains.

Since the primitive people of ancient times could not conquer the rugged mountains, swamps, and dense jungles, the only place suitable for human habitation in Guangxi Province was Guilin.

However, as people paved roads to pull carts and sailed boats on waterways, enabling the movement of goods, they reached the flatlands of Yong, surrounded by high mountains.

Thus, the central city of Guangxi Province, Nanning Prefecture, was born.

As the name suggests, the Guilin Sword School was originally a sect from Guilin.

There are no records left of why the Guilin Sword School abandoned Guilin and moved to Nanning Prefecture.

But one didn't need to have the reasons recorded by their ancestors to know why.

Wasn't it far more profitable to settle in Nanning, a much larger and more developed city than Guilin, in terms of both income and reputation?

After all, it was natural to want to play in a bigger pond to become successful.

And so, they succeeded.

As the representative Orthodox Faction of Guangxi Province, they made a name for themselves throughout the world. To the point where if one mentioned the Guilin Sword School, everyone would at least have heard of it.

Of course, it's still just Guangxi.

To the people of Zhongyuan, the three lands of Guangxi, Guizhou, and Yunnan were nothing more than the outskirts.

So even if one added the modifier of ‘Guangxi Province's Best', it would only elicit a joke like, ‘Wow, do people live there too? What are the barbarians there like?', along with a chuckle.

Still, they were the representative of a province.

The Guilin Sword School was the leader of the Guangxi Orthodox Wulin, protecting the justice of Guangxi today as well…… would be nice to say.

But in fact, as the moon waxes and wanes, everything has its ups and downs. And it was said that no flower could bloom for more than ten days.

Therefore, the time would surely come when even the Guilin Sword School, which seemed to shine eternally, would disappear.

And that time was right around the corner.

"Has the Heavenly Flower Sword not sent any word yet? When did she say she would arrive? No matter how slow the Wulin Alliance is at processing things, this is too much, is it not?!"

A burly man with forearms as thick as tree trunks roared in frustration.

He was the First Disciple of the Guilin Sword School, Dao Daljeon.

"She will arrive soon."

The middle-aged man who could not hide his despondent expression was Gang Suyang, the Sect Leader of the Guilin Sword School.

"When is soon?! The Spring Festival is almost upon us. If she arrives after the sect's signboard has been taken down, are we supposed to expect her to go back and tell the Wulin Alliance that the Guilin Sword School has perished?!"

"It's not something we know yet."

"Ha, and what will she do even if she does come? Everyone knows it's a scheme by those bastards of the heretical factions. Do you think they won't attack because they're afraid of just one Heavenly Flower Sword? Or can we overcome this disadvantage with just one Transcendent Realm expert?!"

It all started a couple of months ago when there was a dispute with a disciple of the Yoga Salt House.

They thought the other party was just a sect that produced salt, but suddenly their membership exploded, and now they had become the largest martial arts faction in Nanning.

Of course, even a fool could see that the Heretical Alliance, the bastards of the Unorthodox Faction, were behind this.

Wasn't it obvious that the Yoga Salt House, which belonged to the Gray Path, suddenly raised the flag of the heretics the moment they gained two elite combat units and a bunch of Unorthodox Masters suddenly switched sects?

And so, thinking that a major incident was about to occur, they kept a low profile.

But five days ago, one of their female disciples couldn't stand idly by when she was about to be harassed and drew her sword, thus giving the other side justification to act.

Thus came the ultimatum.

If they did not take down their signboard and vacate the premises by the end of this year, they would settle things the Wulin way.

"If only the Heavenly Flower Sword had arrived before then, the situation wouldn't have deteriorated this far! No matter what those bastards of the Heretical Alliance say, they wouldn't dare draw their swords against a Divine Dragon of the Orthodox Faction, would they?!"

Dao Daljeon's words had some merit.

If the Heavenly Flower Sword had been staying at the Guilin Sword School, the Yoga Salt House would have paused their provocations and waited.

Then, they could have asked the Heavenly Flower Sword to stay a bit longer and requested martial artists from the alliance, which would have solved the problem.

However, Qing was late.

Now that the ultimatum had been given, if they delayed the settlement because of the Heavenly Flower Sword, the entire Heretical Alliance would be seen as backing down because they were afraid of the Wulin Alliance.

If the Orthodox Faction's face was that of a gentleman, the Unorthodox Faction's face was the ferocity of a wild beast that knew no fear.

Thus, even the Heretical Alliance could not back down from this situation.

"Ahem."

Sect Leader Gang Suyang groaned.

It might seem like First Disciple Dao Daljeon was yelling at the Sect Leader, but in fact, that wasn't the case. He was actually venting his anger on the Sect Leader's behalf.

It was what Gang Suyang wanted to say deep down.

Since those at the level of Sect Leaders couldn't express their anger freely, the First Disciple had to read the situation and vent it for them.

It was then.

"Sect Leader, that fellow is here again!"

At the report from outside, the expressions of both the Sect Leader and the First Disciple turned sour.

Bang! Creeeak, Thud.

The barely nailed door tilted and fell to the ground.

"Well, well, well, this door is too weak to be of any use. Hah. You can use this to fix it."

The rogue who had kicked down someone else's main gate threw a handful of coins from a money pouch he had put his hand into.

They weren't gold or silver, but copper coins.

Like a disturbed beehive, the disciples of the Guilin Sword School poured out.

Among them, Second Disciple Woo Naram drew her flexible sword and shouted.

"You scoundrel! What is the meaning of this?!"

"Scoundrel? Ha, how dare a lowly Zhuang wench point fingers and call someone a scoundrel? Look at this! Just look at the sight of that lowly barbarian wench daring to point a sword at a person!"

The rogue had brought a crowd of onlookers with him, so although they couldn't openly agree in front of a sword-wielding barbarian, there were a few who nodded in agreement.

Of course, one out of every four people in Guangxi were Zhuang, whom they were mocking as barbarians, so there were just as many who were angered by this.

"I have nothing to say to a monkey! Bring your master!"

At this, Woo Naram bit her lip.

It was then.

"Why are you causing trouble in someone else's manor?"

First Disciple Dao Daljeon appeared, his massive muscular body shaking the ground with each step.

The rogue flinched for a moment, but soon erased his frightened expression and put on a vile smile.

"Someone else's manor? Is there a problem with me inspecting my own manor? In just two days, this will be my house. Is there any issue with me looking around in advance?"

"Watch your words."

Dao Daljeon, with a reddened face, spoke politely, unable to draw his sword.

"Didn't I clearly send an ultimatum to vacate the premises by the end of this year? Yet, I don't see anyone packing. If you leave nicely before the Spring Festival, you might preserve your lives. Are you really only going to get your act together once you see blood?"

"You bastard!"

Second Disciple Woo Naram drew her sword.

Although Dao Daljeon raised his arm to stop her, he could not help but grit his teeth in anger.

That insolent bastard was the third son of the Yoga Salt House's leader, Yo Min.

He wanted to cut down that arrogant bastard right away, but that was exactly what the Yoga Salt House's leader was aiming for. That son was just bait thrown out to die.

Of course, since he was a son used as a discard, how incompetent would he be?

So the eyes of the Guilin Sword School disciples were bloodshot, their hands trembled with rage, and their hearts pounded. Yet, they could do nothing but grit their teeth.

At this, Yo Min, a fool who didn't even know he was sent to his death, became even more arrogant, his shoulders rising to the sky.

It was then.

The disciples of the Guilin Sword School turned their attention behind Yo Min.

-Ah, excuse me, can you move aside a bit? What's with all these people? Is there a festival or something? Oh? A festival? Wow, we arrived just in time for a festival before the Spring Festival.

-Don't push, don't push.

-Oof, I'm being pushed. What kind of strength is this……!

As the crowd murmured, a woman lightly parted the men to the left and right as if splitting a reed field, shouting loudly with a cheerful voice.

"Never again, a festival! Pork, beef, lamb!"

Because of that, a woman appeared, shouting loudly with a cheerful voice. 