\chapter{But You Said I Could Play Around? (7)}

If things went this way, it would be as if they had boldly attacked only to offer New Year's greetings to that bastard Gang Suyang, and even worse, to bow deeply in front of all the experts of the unorthodox faction.

But it wasn't as if they could just stand their ground either.

He was, after all, a Prince.

Even if he was a fake, impersonating a royal, the laws of the land dictated that he should be treated as a superior, at least for the time being.

Whether he was a real Prince or a fake one, as long as he claimed to be a Prince, he had to be treated as such unless there was very clear evidence to the contrary.

After all, the very attitude of doubting the bloodline of the Emperor was considered an act of treason.

However, they didn't have to feel wronged for being deceived by some audacious imposter daring to impersonate a member of the Imperial Family.

The authorities would never, ever let someone impersonating a member of the Imperial Family off the hook.

Even if a notorious killer stained the martial world with blood, the authorities would proclaim their policy of non-interference in the affairs of Wulin. However, if someone impersonated a member of the Imperial Family, even if it was just a naive seven-year-old child, they would be hunted down to the ends of the earth and killed.

Even so, Yohwancheol couldn't sleep at night.

It was because of a sudden thought that struck him.

When the Prince went out, I should have bowed once more to that bastard Gang Suyang!

After bowing like that, I should have boldly declared that I would eventually send him to the afterlife myself, so I was offering my condolences in advance! How cool and elegant would that have been!

But it was always after the fact, lying in bed after returning home, that one came up with brilliant ideas. This was a common trait of those who were bad at verbal sparring.

The unorthodox experts also sat with their heads together in the guest hall, looking grim.

"A fake, he must be a fake Prince."

The self-proclaimed master of military strategy, Baekungdan Leader Jo Gwangang, spoke.

Baekhodan Leader Moon Jeongyeok sneered.

"Would they dare to impersonate a Prince just to escape the immediate situation? Would such fools become a sect representing a whole province's capital city? I understand your frustration at being so elegantly deceived, but at least make sense."

At that, Jo Gwangang chuckled, raised his index finger, and shook it from side to side.

"That's why they say not to converse with those who haven't read the Art of War at least three times. According to the Thirty-Six Stratagems, under the Empty Fort Strategy, it says to use everything that can be used in the stratagem of Replacing the Beam with Rotten Timber. Also, under the Losing Battle Strategies, it says to deceive the enemy by sacrificing a part in the stratagem of Inflicting Injury on Oneself."

"It looks like everything is about to be burned, not just a part."

"No, no. Ha. This is why those who don't read military books… I have to explain everything one by one, you see."

Jo Gwangang clicked his tongue.

"Isn't it obvious to have a loyal subordinate impersonate a Prince, and then later cut the tail by letting him die? Understand? This is the 'Inflicting Injury on Oneself' strategy."

"What loyalty when their entire clan is about to be exterminated? Would you do it? Risking your entire family? Make sense."

"That's why it's about using everything that can be used. This is the 'Replacing the Beam with Rotten Timber' strategy. Please, try to live with some thought. When I return, I'll lend you my copy of the Art of War, so be sure to read it and take it to heart."

Moon Jeongyeok's forehead vein bulged clearly.

"Fine. Then let's make a bet. I bet the Prince is real, and you bet he's fake."

"Hmph. You think I wouldn't dare to bet? So, what, you want to bet an arm or something?"

"Let's bet on our monikers instead. If I lose, from then on, I'm not the Supreme Sword of Bokju but the Retarded Idiot of Bokju. If you lose, you're not the White Lotus Iron Fist but the Always Losing Strategist Jo Gwangang. How about it? Well, if you think you'll lose, you don't have to accept."

At that, Jo Gwangang also flared up.

"Ha! You think I wouldn't dare if challenged? Just don't go back on your word and make a fuss later, claiming it was nothing."

"You're the one who should worry about that. And actually, Always Losing Strategist would be a fitting moniker, wouldn't it? You're always spouting nonsense about strategy, but I've never seen you get anything right."

"Did you hear that, Master? You will be the witness, Master."

"Hehe, how could I miss out on something so interesting? But then, what are you going to do now? Are we just going to wait until this Prince, or this Prince imposter, leaves the manor? According to your claims…"

The three leaders shut their mouths.

Of course, Heukwoongdan Leader Sa Heun had been silent all along.

It wasn't because Sa Heun was taciturn.

It was because combat units with the character ‘White' in their names were higher-ranking units and those with ‘Black' were lower-ranking units, so Sa Heun wasn't in a position to speak up.

Anyway, Sa Heun included, everyone seemed to be struck by the words of Master Boyeol.

If they just waited like this, their mission would be a failure, wouldn't it?

The Gulin Sword Sect had likely already sent messengers to the Wulin Alliance, requesting support.

If the Prince stayed here for too long, the plan to use the Yoga Flame Room as a foothold to establish a solid foundation in Guangxi would be ruined.

They couldn't afford to wage war with the Wulin Alliance just to take over the barren Guangxi Province.

"And even if the Prince leaves or somehow disappears, what about the Heavenly Flower Sword? It seems there are some bold strategists in the Wulin Alliance too."

The Heavenly Flower Sword was a Divine Dragon.

To say that she was the best among the Rising Stars of the Orthodox Faction meant that harming her would be like tarnishing the reputation of the entire Orthodox Wulin.

But since the work of Wulin ultimately involved using swords, sending her alone into such a dangerous place was a bold move.

"Hmm, if Master takes on the role of the Sect Leader, the three of us will capture the Heavenly Flower Sword. After taking over the manor, we can release her. What can the Heavenly Flower Sword do then? She'll just go home. The Wulin Alliance won't wage war over that, and if they're really angry, we can just apologize."

Jo Gwangang answered.

Attack first and release later.

It was the same logic as when a certain militaristic nation in Qing's homeland bombed a certain bay.

The reasoning was even the same; since they'll probably hate war, if we just apologize, they'll probably let it slide.

It was said that people's thoughts were all similar.

Especially the thoughts of the shameless bastards.

"Fine. Well, you all do as you see fit. I have my own plans, so I'll move separately. If things go well, it's all thanks to me, and I won't be sharing any credit with you."

You do as you please.

I will do things my way, and I will move separately. So if things go well, it is all thanks to me, and I will not be sharing any credit with you.

At that, the three leaders thought to themselves.

What a cheap old man.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was currently receiving the most exceptional treatment.

They even assigned the esteemed First Disciple as her handmaiden, so it couldn't get any more exceptional than this.

Of course, it wasn't the Sect Leader's personal instruction, but since the First Disciple had volunteered to be a handmaiden, it would have been a matter for a severe reprimand under normal circumstances.

However, not saying anything was also a form of permission.

Moreover, from Qing's perspective, her handmaiden was very talkative, burdensome, and, above all, noisy.

"Senior Sister! Isn't the weather truly clear and bright from the start of the year! On such a fine day! Namnyeong is known for its Cheongsu!! Cheongsu is synonymous with Namnyeong!! How about ascending Cheongsu Mountain to enjoy the scenery!!"

"Even if it doesn't seem like it, I'm still recovering. And you want me to go hiking?"

"Whoops!!! This young girl forgot for a moment! Since Senior Sister is so robust, I momentarily overlooked it! Then, what about Gahwa Fortress! What about Gahwa Fortress!! It is said that bathing in the hot springs of Gahwa Fortress since ancient times brings longevity without illness! It drives out diseases! It rejuvenates the skin! It even cures sores! It is the best hot spring!!"

"Ah, hot springs? There are hot springs?"

Qing's eyes lit up.

Soaking in a hot bath was one of the three great pleasures of this harsh life in Zhongyuan.

Why three? Because if you didn't mention eating and killing, it would be too sad.

And if there were a table in the hot spring, one could enjoy both eating and bathing at the same time, combining two of the three most enjoyable things in Zhongyuan!

Wasn't it the only drug that the nation allowed? (Although there was only one drug prohibited by national law, and that was tobacco.)

"That's a great idea. Let's go right now."

Just as Qing was about to burst into a bright smile, thinking of a hot spring bath…

-Excuse me, Young Lady Ximen. A letter has arrived for you.

A disciple of the sect said from outside, handing over a letter.

Seeing the red envelope in Qing's hand, Unaram made a fuss.

"That is! Could it be a love letter! As expected! The Most Beautiful Under Heaven! The Flower Among Heavenly Flowers! The Reincarnation of Xishi! The Three-Headed Beauty!!"

"Can you please leave out the last one……."

"Ah! My apologies! It just slipped out because I was thinking of three heads! This young girl has made a grave mistake! Senior Sister! This Unaram! I will ask for forgiveness like thiiiiis!!"

Unaram said this and then did a handstand.

If she was given even a slight reprimand, she seemed ready to prostrate herself on the floor. So, as a joke, Qing had said that if she was truly sorry, she should stand upside down in apology.

When asked where she had heard of such a custom, Qing had vaguely replied that it was a form of apology used by the Khitan people, the Khitan's bow, and ever since, she had been doing this.

But rather than seeing her on her knees, it was better to see her doing this ridiculous handstand, so Qing didn't particularly stop her.

"Narami, you can stay like that for as long as you feel sorry."

"This young girl, Unaram! I feel like apologizing for twelve months of the year! Or thirteen months since it's a leap year!!"

Unaram shouted from under her upside-down skirt.

Her well-toned legs were a beautiful shade of brown, quite lovely.

However, Qing's eyes were not in good condition, and after just three days, she couldn't tell whether Unaram was a woman or a wild boar, so it didn't matter much.

Qing held the envelope right up to her nose and frowned, ignoring Unaram.

Ximen Qing.

It's addressed to me. And it's a red envelope, so is it a love letter?

Of course, this wasn't anything new.

Thanks to the saying that the brave win the beauty, or perhaps due to the petty tricks of those who thought ‘if it works, great, if not, oh well', Qing received quite a few love letters.

Qing immediately tore open the envelope.

Just how verbose will this expression of affection be that it makes me laugh?

Generally, the love letters from Zhongyuan men were not very good. They usually followed a certain order: name, praise of Qing's appearance, boasting about their family and car (thoroughbred), and then a generous promise to give her the position of the main wife.

It was as if there was a widely circulated template, and they would say things like how her Young Lady's beauty made their heart race and kept them up at night, how flowers would bow their heads in shame, and how various birds like doves, geese, magpies, crows, mandarin ducks, hawks, owls, etc., would forget to flap their wings upon seeing her and fall from the sky.

I wonder if there will be something new this time.

Qing unfolded the paper.

But there were only a few black letters on the white paper.

A love letter, only two lines!

"Hoo."

Qing brought the letter close to her face like an old man with presbyopia.

And then, Qing's expression hardened.

\begin{quotation}
	「I know your secret. And your origin.
	
	I will be waiting at the hour of the Pig, in the Plum Blossom Room of the Dragon Palace Tower.」
\end{quotation}

My secret? And origin?

Qing's eyes wavered.

What Qing kept secret was the bizarre convenience functions that only appeared to her eyes.

And her origin on top of that?

Qing's mind became complicated.

What is this?

Could there be someone else who came to this world like me?

Qing had no information about the Wulin's Records of Life and Death, so if someone knew more about this world, they might have deduced it just from hearing her reputation.

Or maybe there was another way to find out.

"Narami. Do you know where the Dragon Palace Tower is?"

"The Dragon Palace Tower! No one in Namnyeong doesn't know of the Dragon Palace Tower! If the Dragon Palace Tower is Namnyeong's best inn, then Namnyeong's best inn is the Dragon Palace Tower! It's an eight-story tower that seems to pierce the sky! Truly a skyscraper!! It is the pride of Namnyeong!!"

Unaram answered with only her black hair showing from under her upside-down skirt.

"Are you interested in the Dragon Palace Tower!! But the Dragon Palace Tower is so expensive! No! This young girl, Unaram! I will empty out the allowance I've saved for five months! No!! I will have to borrow money from my comrades! Can I get up now! I need to go to my comrades right away!!"

"No, you don't have to go into debt. Hmm. I see."

The fact that the waiting place was Namnyeong's best inn meant that the sender had no intention of hostility, so she should relax.

It also meant that they didn't want to cause a disturbance in such a famous place where there would be many people. And that she shouldn't cause a disturbance either.

But that didn't mean she could relax.

As such, an on-site inspection was necessary.

She needed to go and check the structure, whether it was possible to escape, and whether any suspicious people had taken over the place.

"Alright. Let's go. And I have plenty of money. Today, let's eat until, um, no, not until our stomachs burst."

After almost bursting her own side from overeating, Qing had become a bit more restrained.

It would be better to recover quickly and eat to her heart's content. After all, if she ate until her eyes rolled back because of the food right in front of her, only to suffer for a long time, wouldn't that be a bigger loss?

After all, it would be a true loss of appetite. 