\chapter{But You Said I Could Play Around? (11)}

The head chef of the Guilin Sword School protested.

"Can't you either reduce the number of dishes or do fewer inspections? What is all this, one by one? I can't take it anymore."

"Chief Kang, do you think I want to do this? What can I do when orders come from above? If they tell me to do it, I have to do it."

The junior chefs, who were peeling a mountain of onions in a corner, nodded in agreement.

Yes. Of course, if they tell us to do it, we have to do it. It's only natural.

After a year of peeling onions and another year of peeling garlic, one might finally get a chance to touch a ladle. That was the strict law of the kitchen.

Of course, even after two years, one was not free from onions and garlic. Thus, no matter how much one peeled, onions and garlic were eternal friends of the junior chefs.

The head chef's eyes blazed at the sight of the rods being poked into the dishes he had prepared as if they were his own precious children.

‘Why can't they just eat it deliciously? Why do they have to keep doing this, saying there might be poison?' he thought.

The Guilin disciples who were conducting the poison tests were also uncomfortable.

Because of this, the task of moving the dishes had been changed from the servants to the Guilin disciples, just in case.

This was all because of a single anonymous letter that had been sent to the Guilin Sword School.

「A cunning viper has infiltrated with its venomous fangs, so please be cautious.」

Naturally, the heart of Gang Suyang, the sect leader, sank when he read it.

‘I was being too complacent and careless while hosting such important guests!'

Thus, an emergency, no-poison countermeasure operation was underway indefinitely.

However, the letter had arrived ten days ago.

There wasn't even a suspicious person, let alone a viper.

After all, the servants currently in Guilin were those who had stayed, not having left even when the evil sect was attacking and saying that the Sword School was doomed. They were loyal servants, the true gems that could be called family even if they were just servants.

Gang Suyang thought.

But when is that viper coming?

Does that viper even exist?

That viper is just wasting the Sword School's food.

Furthermore, they were gluttons among gluttons, eating triple the amount of food, truly the king of parasites.

Of course, if Qing's acquaintances heard this, they might say that only three times the amount of food was an enormous underestimation, but when the quantity increased, the price naturally decreased.

And so, that king of parasites was currently surrounded by her fanatical followers.

"Aigooo, Young Lady. Have you been well since the last time we met! I heard the news. If it weren't for you, we would have been in big trouble. If His Highness had passed away, this old servant would have gladly followed him to the grave. Thus, you are the benefactor of His Highness and the benefactor of this old man. This old servant will repay this debt for the rest of his life. No, how much longer does this old man have to live? This young lady here will repay the debt for this old servant."

"Me……?"

The suddenly indebted Changyeo made a bewildered expression, as if asking, ‘Why me?'.

"Hehe, do you remember this old servant? This old servant is Chang Nankeumho. Although this old servant is just a swindler, no better than a beast, I have received a great favor from you. This body must serve His Highness, so Changyeo will repay my debt as well."

"No, but why me again……?"

And beside her was a lanky man.

"Oh, that sounds good. Changnyeo-in1, you can repay my share too- Eek! It hurts, it hurts! Why is a wench so strong?!"

"Don't you dare mess with me."

"Hmph, I had a dream last night where a beautiful ruby the size of my fist shone with an auspicious light, then turned into a vermilion bird and flew away."

"Is this bastard only capable of dreaming about vermillion birds? Also, you didn't sleep last night. Did you fall asleep with your eyes op-"

"Excuse me, this is a small token, but……"

A man with shaggy hair reaching down to his nose, leaving only his lower face visible, stealthily offered a dagger scabbard.

It was the second most favorite gift for Qing.

For reference, the first was delicious food.

"Oh, a dagger. Thank you. I'll use it well."

"I just picked it up on the way, so there is no need for the noble one to thank m……"

"No, wait, there's not a single scratch on the blade. It's brand new. Where would something like this be just lying around? I need to know so I can go pick, hm? What's this? Déjà vu?"

"That damned fly is bribing again!"

"How did that cheapskate prepare it all by himself! He's carrying bribes around with him!"

"Ahem, I couldn't prepare a proper gift in time due to the circumstances, but if you enjoy calligraphy and painting-"

"Wait, Your Highness?"

At that, heup, the retainers of Prince Deokhyun's residence simultaneously shut their mouths.

Then, they glared fiercely at the man dressed as a scholar who had made the slip of the tongue.

"I, Yeon Pa. Gang Mo greets Your Highness."

When the man dressed as a scholar bowed his head, the other retainers also fell to their knees and bowed.

"I told you, I have no intention of becoming a princess, so please stand up. And Yeon Pa, you have quite a loose tongue, huh? I didn't think you would be like this."

"It is because this old servant finds Your Highness to be the most terrifying person in the world. Please do not be too angry."

"No, it's not like that."

It had been twenty days, or rather, nineteen days since the retainers of Prince Deokhyun's residence arrived in the middle of the night.

They were still as boisterous as ever, treating her with utmost respect. At first, there seemed to be over a dozen of them, but now there were only eleven, so the number had decreased.

"What are you all doing, not doing your work! If your hands are idle, find something to do. How dare you barge into a lady's room first thing in the morning and make a fuss! Get lost, all of you! Ah, Changyeo-in, you stay."

Eek, the retainers of the royal household flinched.

It seemed Yeon Pa was still quite scary, as the retainers of the royal household bowed their heads and quickly scurried away.

"I'm sorry, but, why are you spreading such rumors when I said I have no intention of becoming a princess?"

"This old servant was worried that some lowly ones might offend Your Highness, so I did that. They may seem frivolous and incompetent on the outside, but they have realized how terrifying the sins that come from the mouth are, so please do not worry, Your Highness."

"Hmm."

It was a respectful attitude that came from genuine concern, not just a pretense. It was a kind of emotion that cared for her.

Qing immediately softened.

After all, she was weak to such treatment.

"This old servant was deeply concerned that Your Highness did not have a single handmaiden to serve you, so I thought this Changyeo-in, although lacking in womanly virtues, is still a woman, so you could treat her like a convenient beast of burden. Changyeo-in will also do her utmost to serve you."

"Ah, me……?"

Changyeo-in was startled and made an aggrieved expression.

At that, Qing shook her head.

"Eh, it's fine. Why would I need someone to wait on me? I'm more uncomfortable with servants and things like that. I'll just accept the thought."

If the members of the Divine Cult had heard this, even the followers would have questioned what kind of nonsense she was spouting.

After all, in terms of being waited on, she was a human who had come close to being the best in the world.

But Qing was being serious.

In the case of Gramps or her sworn sister, Qing was the one who ‘allowed' them to wait on her.

It was because they begged and clung to her, pleading to let them serve her, so she had no choice but to grant their wish.

Yeah. That's right.

How can a person order another person around like that?

But speaking of my sworn sister, it's been a while since I saw her……

She said something about closed-door training? I wonder if her realm has risen? It's not easy to reach the Transcendent Realm, though.

Even if I presented her with a free pass to it, it would be difficult for her, especially since she has spent a thousand years in closed-door training.

Well, it can't be helped.

When we meet later, I should impart some of my wisdom to her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Today's schedule was to climb Mount Cheongsu.

Yesterday, they had said the hot springs were reserved for some VIPs, so they couldn't go.

How dare they monopolize a hot spring meant for everyone (not really). Just as she was about to express her outrage, she was told that those VIPs were the sons of a prince, so what could she do?

Of course, a mere prince was a whole rank and a half lower than an imperial princess, who was of the same rank as a prince.

The reason it was a rank and a half lower was because if it was just one rank lower, it would be a Great Prince, and only the eldest son of a prince could be on the same level as an Imperial Princess. No, actually, even then, it was iffy since they were of the direct imperial lineage.

Anyway, she had no intention of throwing a tantrum, saying ‘I am the princess of this nation' just to use the hot springs for one more day.

So, they decided to go to Mount Cheongsu, which Unaram had been singing praises about.

However…

The actual impression of Mount Cheongsu was a bit ambiguous.

"What, it's called a mountain?"

"Didn't I tell you it wasn't very high? This is just the right amount to get some exercise!?"

"Shouldn't they remove the ‘mount' from Mount Cheongsu?"

It was really more of a stream than a mountain.

In fact, it was actually treated as just a neighborhood with a higher elevation than Nanning.

Still, there were a few trees left on the highest peak, but when they climbed up, a strangely familiar scene unfolded before them.

Along both sides of the wide trail were various stalls, tea houses, restaurants, eateries, and handicraft shops lined up in a row.

Seeing the banners with large letters advertising Moju and Tofu, Qing asked just in case.

"Is there perhaps a temple up there or something?"

"That's right! Normally, there should be a temple or a Daoist monastery on a mountain, shouldn't there? A temple at the summit is normal! Ooh! Isn't that a profound statement?!"

"Alright. I've seen enough. Let's go back."

There were wooden pubs, tea houses, and chicken restaurants on either side, and a temple on top.

What is this? Did I unknowingly return to Korea? Is this Zhongyuan or is this the Republic of Korea?

"Huh?! You're not going to climb up?"

"I feel like I already know what it's like without seeing it. They'll probably be selling roof tiles at the temple or something. If we're going to have tea and food anyway, there's no need to go to such a place, is there? Also, I bet it's a total rip-off there."

"That's true……"

Although prices were bound to be different at the top and bottom of a mountain, it was still outrageous to set up proper shops on such a well-maintained path on a not-so-high mountain and charge exorbitant prices.

"Instead, don't you know any hidden gems? Like a restaurant that only locals know about."

"Hmm! If it's that! Come to think of it, since Big Sis said you eat anything! Then do you perhaps also like eating things raw!?"

"I do, but why? Your wording is a bit strange, you know?"

"In that case! How about Giant White Worms! It's a specialty of the Yao people and they say it's incredibly delicious!"

"Giant White Worms? You mean, like, a bug?"

"It is a bug!"

At that, Qing's expression crumpled.

"I thought you asked if I liked to eat things raw a while ago, though?"

"That's right! It's this big of a larva! I heard it tastes soft and creamy like cow's milk, with a hint of apple scent!"

Unaram held up a finger.

Not his pinky, but his index finger.

"Naram-ah, do you… eat that stuff……?"

"I can't eat it! It's disgusting, isn't it?! But if Big Bro will eat it! Then this Unaram! Will bravely cheer you on! From your side!!"

So, in the end, she was saying that she wouldn't eat it.

What's this? Normally, shouldn't she be saying that they should try it together?

How much does she not want to eat it to muster up courage just to cheer?

"Never mind. Let's just go to a tea house and munch on some snacks. Do you know any good places?"

"I'm sorry! I'm not well-versed in snacks! Isn't seeking out snacks just too girly?!"

"No, then what about Naram-ie?"

"I am a martial artist!!"

Qing tilted her head.

It was a declaration filled with pride and confidence.

Even though she kept saying Big Sis and Respect, she had a feeling that something was gradually shifting in a strange direction.

Of course, Unaram continued to be Unaram.

But before that, wasn't there a pathetic glutton who spent his days lying around, eating, drinking tea, eating snacks, soaking in hot springs, then coming back to eat, drink tea, eat snacks, and spacing out whenever she had free time?

If anything, Unaram, who still expressed her respect, should be the one to be respected.

Thus, Qing, who had changed direction from exploring local specialties to snack hunting, was wandering around the bustling streets of Nanning in search of a tea house with a large crowd when…

Crash, bang!

The sound of something breaking and shattering rang out loudly, followed by a scream and sharp curses.

Huh? This is? A sign of commotion?

Are there bad guys? Are there bad guys?!

Suddenly, she wasn't interested in snacks, food, or tea anymore. Instead, something else, the smell of blood, a burning sensation, and a thrilling, pulsating taste, was desperately craved.

Ah, come to think of it, it's been a while.

A bright smile bloomed behind the veil. 