\chapter{But You Said I Could Play Around? (2)}

Before Qing embarked on her journey, she had seen an interesting picture. A traveler was asking about a festive celebration in some unknown, isolated island country.

What kind of festival is being held?

The islander then replied.

It's not a festival, but a funeral.

Still, this traveler could be excused for encountering an exotic culture from a completely unknown cultural sphere.

But Qing was now in a position where she knew all too well about Zhongyuan.

Therefore, Hua Ak, even for Qing, felt her blood rush to her head in an instant, her face turning red with embarrassment.

Moreover, to think they were serving braised pork, sliced boiled pork, and Dongpo pork!

From the start, she had made such a stupid, idiotic statement.

Of course, braised pork, sliced boiled pork, and Dongpo pork were delicious.

Braised pork, sliced boiled pork, Dongpo pork, and soy-braised pork, ah! Soy-braised pork! She wanted to eat soy-braised pork too, but that wasn't the point.

There was a rational basis for Qing to confidently shout out the three types of Zhongyuan meat dishes (meat dishes) as she appeared.

Originally, everyone was supposed to be lively and boisterous at a banquet.

Even if she shouted about braised pork or soy-braised chicken, it would only cause a burst of laughter.

She was sorry for arriving late, and instead of just jumping into the banquet, she wanted to make everyone laugh and enjoy themselves.

But, well. It was a funeral……..

"My apologies. I am Eon Yeongyeong, a connoisseur of fine meats who roams Jianghu in search of delicious delicacies! Eon! Yeon! Yeong! It's not a banquet after all! Then, I shall take my leave. May you all enjoy white-boiled trotters."

Qing, coughing with a thick voice, spoke very naturally with a lie.

It was clear that spouting the name Eon Yeongyeong had become second nature to Qing.

One could say she had reached the state where Eon Yeongyeong was Qing and Qing was Eon Yeongyeong, a realm of Eon-Cheong fusion.

Qing took a step back, then another step back, then suddenly, Wham! She dashed forward with powerful force, fluttering her robe as she soared into the sky and disappeared.

A deep silence settled in the hall.

What was that just now? Was she crazy? No, she was definitely crazy, but was she the daughter of Zhenzhu Eon? What was her name again?

Was it Eon Yeongnyeon? Eon Yeongnyeon?

How can a person's name be Eon Yeongyeong?

Braised pork, sliced boiled pork, Dongpo pork? They're tasty, but still.

And what's with that parting remark about white-boiled trotters?

For reference, white-boiled trotters are a specialty dish of Guangzhou, the capital of Guangdong Province, which is a neighboring province.

What should one call a woman who suddenly appears, looking for meat and calling herself a beauty?

It was a moment when the infamous title of Carnivorous Glutton, Eon Yeongyeong, might have spread among the people of Guangxi, or maybe not.

Regardless, Ximen Qing, a twenty-year-old maiden who had burst through the main gate, no, she had escaped over the wall instead of through the window, hurriedly crossed the main road.

Thus, she headed towards a carriage parked in a corner of an alley over there.

Jayu and Yeon Pa hurriedly ushered Qing inside.

Qing had gone out to ask for permission in advance for a Prince to enter the Guilin Sword School.

(Although it had turned into a situation where the Guilin Sword School had to allow the Prince's visit, Qing insisted that even a Prince should not enter without permission.)

"You're back quickly. Can we go now?"

"No, it's not that. I thought my clothes weren't right. I'm a disciple of the Divine Maiden Sect, so I should wear the Divine Maiden Sect's uniform. Can you close your eyes while I change?"

Jayu's expression turned subtle at that.

"Close my eyes?"

Even though men and women should keep their distance-(the rest is omitted)

It was a topic of contemplation that any man traveling with Qing should ponder at least once.

"Why, do you want to go out and wait instead? It's cold."

"The Young Lady is right. It's cold, so you should preserve your health."

Yeon Pa chimed in, supporting Qing's words.

At the same time, she winked at Jayu repeatedly, causing his eyebrows to twitch.

He had no idea what she was trying to signal.

What is it? Is she telling me to peep or something?

"Ahem, it's just for a moment. Nothing will happen."

Jayu put on a veil and went outside the carriage, while Qing simply took off her clothes as if she was peeling off a layer of overcooked fried batter.

Qing was a master at changing clothes.

If she could change clothes quickly even while holding the sharpest Qingzi Sword under the Heavens, then doing so with both hands free was instantaneous. In a flash, her clothes were changed.

After changing into the Divine Maiden Sect's uniform, Qing stepped out of the carriage again.

"Ah. Jayu. Change my veil for me."

Thus, after changing her veil to become a completely new person, Qing headed out of the alley where the carriage was parked.

Meanwhile, a long silence lingered in the Guilin Sword School's manor, where tension had been rising.

They had not yet recovered from the shock of the Carnivorous Glutton Eon Yeongyeong's sudden meat craze.

"Ahem, let's get back to what we were discussing."

Yao Min, the third son of the Yao Family, who had been cast aside, tried to regain the atmosphere.

"I clearly said to wait until this year, so if you don't want to see blood on a good Spring Festival-"

Then, a murmur from behind.

Should we tell them to make some Dongpo pork for this year's Spring Festival? No, stop it. Do you know how much effort goes into making Dongpo pork? Just, well, sliced boiled pork. Sliced boiled pork is easy. Isn't stir-fried pork belly also good? I heard about white-boiled trotters and now I'm craving it. Shall we have a drink later?

"Shut the fuck up, will you?!"

Yao Min shouted abruptly.

He had come with the command to thoroughly embarrass them by bringing a large crowd to watch, but some crazy bitch had ruined the atmosphere.

"If you have nothing else to say, then leave. It doesn't seem like you have any particular business here."

It wasn't Qing's intention, but thanks to her, the disciples of the Guilin Sword School had regained their composure.

In fact, some disciples were even smacking their lips, thinking about food.

It was much better than trembling with anger, their faces red.

"Hmph, such bad luck. Tsk!"

The atmosphere was already ruined for any provocation.

In the end, Yao Min was about to turn around, spitting on the ground with a swagger, when…

Another veiled woman suddenly emerged, cutting through the crowd of onlookers.

She was tall, so was it that bitch from before? It definitely seemed like her-

However, the veiled woman's words were not kind.

"Who taught you the manners to spit in another's sect? You're spitting in a sacred Daoist temple. Do you also spit on your ancestral rites table?"

The Guilin Sword School was a Daoist sect, after all.

Most sects that ended with ‘School' were considered to be part of the Daoist tradition.

"Hah, what's this now? The Heavenly Flower Wind? Everyone's covering their faces with rags because of that Heavenly Flower Sword bitch or whatever. What a mess."

Now he saw that it wasn't that crazy bitch from before, but a female Daoist wearing a Daoist uniform.

"Hmm."

To prevent the same disaster as before, he asked the onlookers who were craning their necks to peek inside what was going on and heard the gist of it.

It seemed that this bastard had been coming to the Guilin Sword School almost every day lately, provoking them with his words.

"So you're saying that I, this young lady, am like a dog or a cow? Can you take responsibility for those words?"

"Heh, try if you can. But do you think you'll be safe if you touch me? Right now, the elders of the Four Sadoryeon are lending their strength to our Great Nanning Yao Family- Ack!"

Qing's scabbard struck Yao Min's crown.

The Moonlight Sword (No. 10) was a heavy greatsword in itself, and with the scabbard on, it naturally became even heavier.

"There, I touched you. So what now? What's going to happen to this young lady? Will lightning suddenly strike or something?"

"Y-You, you dare! You're dead now!"

"Wow. Am I dead? Is this the underworld? It doesn't seem much different from the living world. Everyone, I'm dead, but how did you all end up in the underworld? The path to the underworld was said to be cold and desolate, but it's quite warm for winter. What a nice day."

Laughter erupted at that.

"I'll kill you!"

Losing his temper, Yao Min drew his dao and charged.

If Yao Min was at the Unrestrained Realm, it might have been a different story, but for someone of merely First-Rate to charge at her, he had far too much confidence in himself.

Thwack!

With a cheerful sound, Yao Min, who had been charging, was knocked to the ground at a right angle.

It was Qing's fiery slap, no, it was a poisonous slap infused with the venomous energy of the White Hand Demonic Arts.

"Argh! You bitch!"

Yao Min jumped up and charged again.

Thwack!

This time, Yao Min was struck on the opposite cheek and sent flying, scattering white teeth.

Only then did Yao Min come to his senses.

A Master. And an incredibly powerful one at that.

He had only realized it now, which was why the head of the Yao Family had sent him to die, knowing he was a fool.

"I-If you touch m-me-"

"This young lady here is the Heavenly Flower Sword, Ximen Qing."

At this, a murmur spread among the crowd.

The Heavenly Flower Sword! The Most Beautiful Under Heaven! The Three Heads of Beauty!

Qing's eyebrows twitched.

No, why are there more and more of these?

Who the hell came up with the Three Heads of Beauty?

I remember that voice, just wait until I get my hands on you.

She suddenly felt a surge of anger.

Fortunately, there was someone in front of her to vent her anger on.

"Have you spat in a sacred Daoist temple? Since what comes from a person should return to a person, why don't you cleanly lick up what came from your mouth with your tongue?"

"That's."

Qing held up her most beautiful hand, one that anyone in the world would agree was exquisite without any objection.

"Now, look here, it's sparkling."

Then, golden threads of Force Qi sparkled.

"What do you think will happen if you get slapped in the face with Force Compression? Aren't you curious? This young lady is really curious."

"Hiiiik."

With a pale face, Yao Min finally knelt on the ground and licked the ground.

After licking up a layer of dirt, Yao Min swallowed the sand that filled his mouth with a grimace.

Then, just as Yao Min was about to get up, Qing placed the tip of the Moonlight Sword in front of him.

"D-Did you not say to do as I was told?"

Then, Qing's sword slid to the side, pointing at the ground.

"Ah, was it there? It's not there, but here, here."

"Isn't this where the spit landed? Why are you licking the innocent ground?"

"Ah. Right. Is it here? It looks like sand here, not a rock?"

"Ah. It's here. My apologies."

"In fact, it doesn't matter where, so why don't you just keep licking the ground until I say it's okay to raise your head? It's said that even rolling in a dog shit field is better than the afterlife, so wouldn't it be better to live, even if you have to lick dirt, than to die?"

At that, Yao Min diligently licked the ground.

Now, Yao Min would never be able to escape the label of being the one who crawled on the ground and licked dirt until he died.

His title would probably be something like ‘Earth-Licking Dragon', and he would never be able to surpass such a level.

Of course, it wasn't just Yao Min's disgrace alone, as this was an act that thoroughly shamed his sect and family as well.

If an ordinary martial artist had suffered such humiliation, they would have charged and demanded death rather than endure it.

However, this fool, who didn't even know he was sent to die, seemed to want to live at any cost.

But why are they still just watching even after all this?

Qing glanced at the disciples of the Guilin Sword School.

They were just staring blankly at Yao Min crawling on the ground with stunned expressions, but their lips were strangely loose.

"Ahem."

Qing cleared her throat needlessly and made an exaggerated gesture towards the largest of the Guilin Sword School disciples.

It was an obvious hint.

Only then did the large man snap out of it, stepping forward and opening his mouth.

"Stop, that's enough."

The head disciple, Do Daljeon, intervened with a tone filled with laughter.

And he continued.

"If it were me, I would rather bite my tongue and die than disgrace my sect and bring dishonor to my family by crawling on the ground and licking dirt. So let's stop. I'm asking you to stop."

His words were meant to stop the situation, but in reality, they were meant to be heard by everyone.

"Since the owner of the Daoist temple is asking like this, I have no choice. I will show you special mercy."

Qing played along.

This way, it would seem as if the Guilin Sword School had saved Yao Min by intervening on behalf of Qing.

On the other hand, Yao Min had come to cause trouble, only to end up showing the world his most pathetic side and even owing a debt, a truly remarkable achievement.