\chapter{Journey to Beijing (1)}

Today, the peaceful Yizheng Martial Study Hall was here again.

The swordsman was still running wild.

It's a martial arts school, what's the point? Originally, martial artists had to be more enthusiastic than others. Shouldn't they at least be enthusiastic instead of using their brains to fight without weapons?

And in the main hall, the sound of mourning rings out.

The extreme training and hellish experience of Peng Cho-ryeo, who was held responsible for the defeat in the Battle of Manbyungjiwang, unfolded.

-Beep beep beep forty! Aaaah… … !

-Who gives the final command? What's with this reaction? Aren't you Guan Yu? You can't even cheer me on, but you're trying to blame me? Don't you come to your senses? Let's start over. Lift your feet!

The poison that Qing unleashed on the Zhongyuan, the training method of the world's most elite guerrilla unit, was a great training ground where only the cries of "Kill me instead" resonated.

He was the master of daring to venture into the business of love in the sacred academy, the cradle of precious learning.

And the second outing.

Since most of the swordsmanship instructors have returned to going out, it has become difficult for me to go out and play as an instructor.

But Qing had a reason to go abroad.

Shouldn't we go and catch Danjoya, the leader of the three idiots who claim to be the brains of the so-called Shiksim Demon Army and the closest of their associates?

However, the moat that they arrived at first with surprising lightness was eerily quiet.

Qing knocks and gropes the jade.

Why, they dug their base underground during the martial arts competition, and they even dug up a stone slab in Nosan, so I wondered if they were the kind of people who liked to dig up the ground.

And as expected.

A subtle echo in an ambiguous corner of the room means that there was an empty space underneath.

Isn't it Qing, who has been taught the keen senses of transcendence and the methods of searching passageways and secret hideouts as a prospective divine warrior?

Qing gently traces the floor with her fingertips, then suddenly pushes her fingernails into the very small gap that she encounters.

Inside there was a box and a letter.

"His Mahou has arrived. He may be carrying out some kind of operation. However, our objectives have been achieved to a certain extent, and we may be caught up in the Mahou's own operations. Therefore, I will go to see my lord and inquire. Instead… "

Miss, this kid, what was he doing?

Looks like I'm a beat late.

But if you say that the reason you left your seat was because of a White Hand Witch, you were like a witch from this evil blood cult, I will never forgive you.

Even if it's a letter, if it's written like this, it's not even evidence.

Mahu? Are you talking about Sosumahu? This Blood Cult guy, he's caught. Just tell him. I have to try.

Just a moment, a misunderstanding. Jang Ma-hoo, someone I personally respect. That's the end of it.

Hmm. If that's the case, I should have stayed behind and watched our hard-working officials' martial arts performance instead of going out…

But the kids will come down, and Jangmyeong and Ciyu will be here too, so they'll arrive around dinner time.

Even if they were friends, I have to take care of Jangmyeong and Ciyu, right?

There's really nothing I can do. I'd love to go back, but… Ah, I'm forcing myself to cook, drink, and be a nuisance to these guys…

However, Qing flies away with a bright smile on his face.

In the originally shabby thatched house, only the shabby interior remained, just like its exterior.

And time passes, and a dark shadow falls over the already dark room.

How much time has passed like that?

To be exact, the time it took for a master of lightness, one of the few in the entire Zhongyuan, to descend the mountain was the same as the time it took for an ordinary second-rate warrior to slowly walk down the mountain.

Finally, the door opens and new characters appear.

Three young men with very nervous expressions.

But contrary to his tense expression, he enters the room and heads towards the hidden floor as if it were natural.

So the secret floor opens again, and the three who discovered the letter on the box see each other.

And soon, the three heads come together and read the letter together.

"Your Majesty… … (omitted)

… … I will go and inquire with my lord. Instead, I have prepared money for you. Use it to provide him with food, wine, women, and gifts to gain his favor and popularity.

The expressions of the three young men, the three fools of the Blood Cult, brighten as Qing speaks.

Well, that can't be helped.

It was the first time in a long time that I saw a difficult boss.

But wouldn't the boss have left the money behind, telling you to go out and buy some delicious food with your friends instead?

Anyone in the world can't help but be happy.

So, the three fools, who had become excited, opened the box with great force.

Clearly, if it was enough money to buy popularity and favor by offering drinks, food, women, and gifts, it was not an ordinary amount.

Alcohol! Food! Women! The eyes of these three fools sparkle, making you wonder if you've ever seen such intelligent eyes.

And so the box opens.

Inside it-

Just three coins!

``Hmm?'' ``Huh?'' ``What was this?''

Three people rub their eyes.

Even if you look roughly, there were three coins. Even if you shine a lamp, there were three coins. Even if you lift the box and empty it out and knock it over, there were three coins.

What on earth does this mean?

Three coins can buy you three empty dumplings at a cheap restaurant, and according to the rules of the game, if you buy three dumplings, you get a bowl of mulgeon soup for free.

Are you suggesting that the three of us go and each eat a plain dumpling? And drink the soup while you're at it, so we don't choke?

If the three fools had been just a little more educated, they might have been able to recall Xun Yu's story.

Ah, the leader said we were just three coins worth, one coin per person! I could have made a very unfortunate choice.

What would three idiots who grew up in a remote village know?

His face was just turning red and blue, and I don't know what it meant, but he was definitely angry, and he was just grumbling with a hardened face.

The correct answer was that the thief (a prospective newcomer) went there.

``Mahu? Why was that girl there?''

The fact that the Blood Cult-limited Demon King was the Demon King of the Sub-Sim Demon Army was absurd.

Why was that crazy old bastard in Hanam?

As far as I know, weren't you planning a great undertaking in Heilongjiang, the outskirts of the continent?

``Don’t you know anything?''

"Hmm. I don't know. She's such a moody girl. And hanging around with that annoying, savage bitch was just a thing—"

``No, what were you talking about? A bitch who was a rascal? How can you say that?''

At that moment, there was a voice that dared to cut off Subsimma Hwang's words.

As can be seen from the fact that he calls himself Ma-Hwang, Seop-Sim-Ma-Hwang was a madman with great self-esteem.

There was only one person in the world who could stop the words of the 9th Demon King.

"Oh, my. It's stuck in my mouth. The commander of the guard said, "Oh, yeah, I want to eat watermelon?"

"Huh. Don't change the subject. I'll let you off the hook just this once. Ah."

The impudent woman lying down with her head on the knee of the Supreme Demon King was none other than the Supreme Demon King's golden jade leaf, the Supreme Demon King's wife, the Supreme Demon King's wife.

As I put a round, mouth-shaped piece of watermelon into my daughter's mouth, I recall that terrifying and dizzying moment from the past.

ZGVPdDc2cnQxMFU0bVlrbnZITXlVaFBiQ1hBTVNnOVdQUExVdFNJa2owODIwZjRJVWVjRW8weWJoWHdPako0Lw

If only the Jiangshijaeng, or rather the leader of the Shibyeongdan, had happened to be in Hangzhou. I would have almost lost the most precious daughter in the world.

Even now, when I think about it, Heavenly Blossom Sword, that damned woman, I'm going to make sure she ends up in the most miserable state in the world.

``Aha? Hungkarakjong Ppeujing.''

"Oh no. This guy's been thinking about something else. What do you think? I just cut off the best part."

The watermelon slices, cut into round mouth-shaped pieces, were the most delicious centerpiece, so he cut dozens of precious watermelons to feed his daughter.

There was no such thing as a failure to sell.

"Well, you can just ask her directly. Why don't you bring that bitch over?"

That Kangsiyeon refers to the masterpiece of the poet Eon Yeon-yeong, the leader of the Shibyeongdan, the Manri Shintong Gangsi.

The Thousand-Li Supernatural Power was a legendary realm of telecommunication that was said to be capable of transmitting messages over a thousand miles, but in reality, it was a Taoist magic that appeared in stories.

Isn't it the limitation of human beings that a sound cannot travel even half a ri, let alone a thousand ri?

But what about supernatural powers?

But that's what actually happened.

At the mention of Kang Si-nyeon, Yu-ryang's expression instantly turned sour, a deep-seated disgust that seemed to reach the level of murderous intent.

But it passed by in an instant so no one noticed.

Yuryang just mutters to himself.

"Big sister, can you connect me with Yang Jing? But how long do I have to please this filthy person?"

Then the answer came to my head.

[This was too full. But if I act cute, delicious food will pour out. I have a mouth, too. I won't die if I don't eat, though. So, I'll act cute, and you'll lie down in the coffin?]

[Oh, I'm connected. Hehe, unnie, do you like watermelon? Should I go get some later?]

[Reception. Ah, you came to call me. Why on earth doesn't this kid wake me up gently and kick me instead? It's so sad. Some women were born with a silver spoon in their mouths, so they live in luxury even after becoming compatriots.]

Yang Jing, who was dragged out through this process, whets his appetite looking at the watermelon slices, carved like jewels, piled up next to the throne of the Supreme Emperor.

Followed by a transmission.

And somewhere, reception.

"Oh my? A melodrama? When did you sneak out to Hanam? It's so sad. If it were Hanam, it would have been nice to go together."

``What were you talking about? Why was this bitch talking nonsense when she’s eating normally?''

Shinpa, Sosumahu frowns.

The old man was originally a bit of a talker, but he had no particular ill intentions. Sitting across from him, Yeongyeong turned her head and tilted her head sharply.

Her silky hair sways and falls to the side, clinging to her side and obscuring the little zombie who has his face buried in her ear.

``Didn’t the Emperor just ask you a question? He said, ‘Why were you wandering around Hanam, you old man?’''

"Who calls someone old when they're both getting old? And the land of Hanam? Are you asking about that? When was I ever absent?"

Unyeonyoung's head tilts even further at that.

It ended up being quite a strange sight, with the face smiling brightly and bent at a more angle than usual.

"Oh, but you're saying she really was a witch? You say there were more than a few people who saw the magic wand. A melodrama? Oh my, you took in a disciple you didn't even know?"

The minority leader snorted at him.

"Do you think there's only one White Hand Witch? It's a bitch with a grudge who passes down her magic to another vicious bitch. It must have split somewhere between the master's master's master. It's a good thing. If you say you won't learn, and there's a separate lineage, then this old man shouldn't have to worry about it either. He should just embrace the magic and die."

"What, melodrama? Don't you even care? Even though a complete stranger was using the name melodrama?"

"A bitch who's even mastered the magic of magic will probably know how to tear men apart. Okay, just say it's me. Say I stopped by because I was bored."

Not only will I let the impersonation go, but I will also confirm that it was me.

Unyeonyeong clapped her hands in response.

``Oh, if Hanam was real, were you a body double right now? Oh my, it’s really amazing.''

"Don't talk nonsense. How could he have learned the art of sorcery without witnessing some truly horrific sight? He must have had some difficult circumstances, so why bother getting entangled with those Blood Cult guys?"

He was a very kind and gentle man who was gentle to women and even more gentle to strange women.

At that, Unyeonyeong straightens her posture.

"Ugh. This was boring. I was just thinking I'd take this opportunity to see your beloved face. It's annoying. Ah, I miss you."

``Okay. Let’s eat.''

Communication terminated.

And again, the Legislative and Military Affairs Office.

They were officials who sweated every day, with today being the same as yesterday and tomorrow being the same as today.

The swordsman was still burning with passion.

The dance hall was moderately passionate.

However, the atmosphere of the main hall has changed.

It was thanks to a single word from Pang Dae-san, who could not stand to see the officials rolling around in front of his sister's anger.

-I absolutely hate weak women. I'd rather have a strong and sturdy man like you.

Then suddenly the women's energy exploded.

As women grit their teeth and embark on training, aren't they burning with passion, putting effort into strength training that they had previously avoided because they thought it would build muscle?

No matter how much I tried to manipulate them, they didn't come to their senses, but rather just looked weak and cried.

If this was the case, why do we need an instructor?

It was a result that even made Pang Cho-ryeo feel ashamed.

Thanks to this, the men who were tired of the pressure of the women shook their heads, and so they too were able to put aside unnecessary superficiality and focus on training.

As a result, the atmosphere in the main hall was also gradually heating up.

An uninvited guest visited the Jeongmuhak Hall, which was ripening like this.

From the moment he appeared, he was by no means an ordinary guest.

Well, no matter how you package it, a guest who appears in a golden palanquin cannot be considered ordinary.

It was even more extraordinary because he appeared in a golden palanquin and was completely soaked in the heavy summer rain.
