\chapter{Journey to Beijing (4)}

As if the rumor about the elixir wasn't a lie, Wibasun took out a wooden box from the inside of his eunuch uniform's long sleeves.

``This is the Sun Live Elixir.''

He looked down with regretful eyes, and his hand, which he extended little by little, started to tremble.

Just looking at the reaction, it was clear that it was a precious elixir.

However, it was a wooden box that seemed to be slowly being pushed out and then slowly withdrawn, and then slowly withdrawn, but somehow it was hesitant and never got closer.

What is this? Is it an optical illusion?

It seems like it's reaching out, but the distance isn't getting any closer?

But if the other person doesn't come, then I just have to go.

``Thank you so much. How can I possibly repay this kindness…''

Qing reached out and grabbe the top of the box.

Then, the upper body was grabbed tightly.

The blood drains from the hands holding the wooden armor as the one who wants to take it and the one who doesn't want to give it struggle.

``Oh, even though you’re so sick, you’re still very strong.''

``Hehe, I’ve heard a lot of compliments about how strong I am. Thank you.''

``It’s not a compliment, no, no, what power, like a patient who will surely die tomorrow, doing it.''

``Ah, my wounds, cough, cough.''

And yet, the wooden armor floating in the air trembles.

I don't know what kind of wood the wooden chest was made of, but it can withstand the strength of two unmanned soldiers. I don't know if the contents were the same, but the chest itself must be quite a masterpiece.

``Look, you don't look sick at all.''

``Confucius said, ‘Cidaeryiyi\footnote{辭達而已矣; 'The words are clear and that's all'}, Pingfeng\footnote{Folding screen, from another verse of Confucius Analects. In this case, it means using something to hide someone's intent }, uh, what was it? The eunuch has already taken my pulse, so what is the point of revealing my pain?''

The saying 'Cidaeryiyi' was from Confucius' Analects, chapter Duke Ling of Wei, meaning that words were enough as long as they were understood, and there was no need to exaggerate or embellish them.

In other words, 'you already knew that I'm sick, so why should I pretend to be sick? You took my pulse, you know?'

The tendon on the forehead of the upper jaw was convex.

Although he was a man who prided himself on his military prowess, his teeth were clenched as he exerted all his strength, and his voice came out loud, which was not befitting of a eunuch.

A woman who was sick, yet shows an ignorant strength that was not inferior to him, yet her expression does not change and her speech does not slur. What kind of strength was this?

Moreover, she even wrote text messages that were not suitable for a woman who was only strong and ignorant.

And the girl who can recite letters fluently can't even remember one thing, so what's with the folding screen?

The eyes of the one who wants to take (take) and the one who does not want to give (give) meet, and sparks fly.

The upper body becomes excited again without realizing it.

Princess Yeonsul, who had a good appetite, was served small portions of food by the emperor's strict order.

It was an imperial edict issued because the already large woman should not grow any larger.

Because he was always whining about being hungry, it was a daily occurrence for the eunuchs to offer him snacks.

If you suddenly grab it while giving it to him, wouldn't he have tried to take it away like this?

Then, when the time was right, let go.

The blue was curled up behind me.

Miss, I have to tell you and let it go.

Anyway, the elixir was mine now.

Qing lies face down on the floor and quietly puts the wooden box into her bosom.

Then lie down and rub your forehead.

``Oh, I’m dizzy. I can’t get up.''

If someone saw me, they would ask what on earth I am like now and what kind of guts I have to act like a dog in front of a high official.

Qing's innate sense, cunning to see the state of others, especially those of an older generation, and to ride the line.

The instinct of the legendary old man murderer was telling me that now was the time to crush and tear him apart like this.

The gaze of the upper body was directed towards Qing, but the place it was looking at was a past, a memory from some time ago.

What kind of princess in the world would do that, lying down and barely managing to put a snack in her mouth?

But soon, Wibasun's eyes take on a cold light.

Well, Princess Yeonsul was still alive and well.

If Princess Yeonsul had died, these memories might have blossomed into a faint sadness, but Princess Yeonsul still exists.

It's just that people have changed.

From a cute and lovable Jin-sang to a difficult and demanding superior, and from a loudmouth who was once unbelievable as a princess, she has now found her place as a virtuous royal lady. So, you could say that the change that was supposed to happen has come, albeit late.

You can see someone who resembles the dead, and miss them by following their footsteps.

But it was only a reminiscence of the past of someone who was still alive and well, and our princess was cute in the past.

That was only natural.

When you see the blue, you think, 'The princess of the palace who was alive and well was fake, and this person must be the real one. There must have been some kind of conspiracy behind this.'

It's not a matter of having a good sense or anything, but it's closer to a delusion that borders on dementia or mental illness.

The moment Wibasun's gaze changed, Qing quietly got up as if nothing had happened and took a proper posture.

What the heck, this old man, his mood keeps changing.

What kind of bipolar disorder were these?

Well, um, that could be it. If you look at it, um. Since you're a goner, you know, menopause, something like that?

As I was doing that, Wibasun suddenly showed a mean smile, and his eyes were sparkling white, and there was a kind of murderous aura about him.

"Oh, Heavenly Blossom Sword. Even if it's a very important detail, it seems that it's not very good for a woman to lie down so frivolously. However, I will protect you, so please take the elixir immediately."

The time when a person takes the elixir was one of the most vulnerable times.

``Oh. Is that so?''

Qing immediately opens the lid of the wooden box and quickly pours the elixir into her mouth.

Then, he sits cross-legged, puts his hands together, closes his eyes tightly, and takes a deep breath.

Oh, hot, no, scorching, wow, hot?

As soon as the elixir was passed, a thousand Buddhas rise up inside of me.

This was so hot that no other drink can match it, I wish I could just eat it all up.

Well, it's a medicinal elixir with extreme properties.

The energy, like lava, explodes and spreads throughout the entire energy vein.

Originally, a potion that was so extreme in one direction should not be swallowed carelessly.

It was designed to be taken when the balance of yin or yang was disrupted and one side needs to be urgently supplemented.

Or, it was an item that was made by taking a pair of extreme negative elixirs together, using the principle of symbiosis.

But Qing was fine.

Wouldn't it be enough to focus on the yang energy among the various internal energy methods you've learned?

Even if we exclude the studies that have already reached the Twelve Constellations, there was still a considerable amount of capacity left for the positive nature of the Yongsan Banyahosimgong, the Mansangyeoilsingong, and the Blood Demon Kingsingong.

Besides, this was a really good elixir… … .

The medicinal properties were also quite rich, and like other medicinal herbs with yang energy, they all have the medicinal effect of boosting vitality.

Wibasun blinked his eyes.

What the hell kind of crazy woman was this?

It's like the annoying temper of an old eunuch.

A eunuch who has had his scrotum cut off always lacks yang energy, and any eunuch who takes a medicine with extremely yang properties that can replenish that yang energy would inevitably drool.

He received the elixir from the medical school, thinking that he might use it, but when he became a eunuch in charge of the military, he would use it even if he didn't, so it was not that difficult to take care of it himself.

He had already given me the elixir that he had secretly considered his own, so he was acting like a sullen man and telling me to drink it here while he was still alive.

But, what on earth does this woman believe that makes her eat it up like this?

She's already a seriously injured woman, so what if she gets beaten to death?

Since the internal injuries were serious, if I can't treat it, I'll die anyway, so I guess I'll just swallow the elixir first.

Or maybe he was convinced that since the Emperor had called him, he would not be able to touch me.

Or maybe it was because I was momentarily lost in my memories that I came to think of it as harmless.

Either you have a lot of guts or you were very cunning.

Or maybe I was too naive.

The upper body was tilted upwards.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the Zhongyuan, no matter how expert one is, one would never set out on a mountain path in the pouring rain at night.

No matter how sharp your night vision is, you can't see anything on a pitch-black night, and when it's pouring rain, you can't even be sure of a light, so you just have to sleep soundly and go out in the morning.

Last night, before leaving for Beijing, I got together with my friends for the first time in a while and chatted a bit.

Although the egg was still firmly entrenched, our baby was also acting as a bed (pillow included).

So morning.

Qing found the guest house.

and.

\textit{Um, this old man? No way?}

\textit{Are you going to resent me for taking the elixir?}

``Why were you doing that?''

``Uh… how could I get into the palanquin without you, sir? I’m fine…''

"No. Your medical history isn't even good, so why would you make a patient walk this mountain path so harshly? Don't hesitate, just sit down."

Qing looked at the golden palanquin with a sour expression.

Gold isn't a strong enough metal to support a person's weight, so it would be plating.

This was really really shiny, what was this shiny, shiny, really shiny, the shine was dazzling.

The academy's warriors were not without reason shocked.

The golden palanquin boasted a vivid golden color even in the pouring rain and gloomy weather with clouds.

If anyone sees me riding in a palanquin like this even once, I will be given a punishing nickname like Golden Dumpling Man or Pure Gold Dumpling Association for the rest of my life.

In other words, it's extremely tacky!

He feels like a total nouveau riche, with bad taste and even worse taste, like a pathetic nouveau riche.

Besides, it's raining today too.

Shoooooooo-!

It's pouring down a lot.

``Uh… doesn’t this have a lid or something? It’s like it’s detachable or assembleable….''

"Isn't this a splendid golden palanquin, a sight for all to gaze upon? If it were to obscure the top, it would cast a shadow. And if gold shines brighter than people, why bother using such expensive gold?"

It meant that there was nothing to obscure the sedan chair, as it was intentionally made to focus attention.

What can I do? When Qing was about to head to Geumgyo-

"The Heavenly Sword. Didn't I tell you? It's a golden temple that all people should look up to. If you were to ascend a place reserved for heroes in such attire, how would the people regard you?"

``Oh, it’s raining like this?''

Qing asks awkwardly.

Such attire refers to the raincoat, or sai, of the Zhongyuan.

I have to go in this rain without even a raincoat, in a palanquin without a lid?

And it's not just rain.

Raindrops the size of a raindrop would make you feel cold if you hit them, and even if you take a bath, wouldn't that be the kind of rain that makes you exclaim, "Wow, that water pressure was really good!"

Qing tries to protest first.

``My health was not good, so even if it was summer, I cannot stand being exposed to cold rain. If I get hurt, it will be a burden to Your Majesty to call me…''

``It’s okay. Okay. I’ll put it on for you.''

``Oh, you yourself?''

Wibasun opens his umbrella.

It's called an umbrella, isn't it? The huge umbrella the servant was holding when the imperial edict was read yesterday. Isn't it the kind of giant object that would be stuck on an outdoor dining table or on a sandy beach in the Qing Dynasty's homeland?

The blue became a little more uncomfortable.

The golden palanquin was a matter of my dignity and face, but this is, what should I say, a matter of respect for the elderly? Or elder abuse? Of course, he's not an old man of low standards.

Wibasun smiles brightly at him.

Anyone could tell that it was a fake smile, and it was truly a smile with a lingering aftertaste.

Qing climbs into the palanquin with a shit-eating expression.

Even though this was gold, it's hard…

And on the way out, even in this rain, there were swordsmen lined up on both sides.

``Instructor! Have a nice trip!''

``Instructor! I’ll be waiting!''

``Oh, Instructor! My Instructor!''

At the end, who the hell was that guy, who's like, you should be climbing on the desk, um, you're a dog, you're the one. Why am I your instructor, um, I guess I'm your instructor.

Even in the pouring rain, Qing-i was greeted warmly, and he quietly turned his eyes away.

Everything was fine, but I can't help but feel uncomfortable riding in that old-fashioned, gold-plated palanquin. Who on earth made this?

Isn't this made to be a side dish?

Anyway, like this.

Departure to Beijing.