\chapter{Journey to Beijing (3)}

There was a saying in military strategy that if you want to deceive the enemy, you must first deceive your own army.

In Qing's hometown, many people believe that this saying comes from Sun Tzu's The Art of War, but it actually comes from the Thirty-Six Strategies, an ancient military strategy of unknown author.

And no matter what anyone says, isn't the greatest ally yourself?

If you want to deceive the enemy, deceive yourself first!

So, Qing keeps repeating this to herself.

I'm sick. I'm very sick. I'm like a corpse, a breathing corpse, on the verge of death. I'm in pain all over my body, and I feel like I'm going to die…

Then, little by little, his shoulders slump weakly, and his usually energetic expression loses its energy, taking on a sad and sorrowful look.

Originally, her skin was incredibly white, and her gloomy expression made her look pale and sickly.

In fact, for the Qing people, over-immersive malingering was not a very great skill.

In the Qing Dynasty's homeland, there was a culture of honing the art of pretending to be sick from a young age to win personal freedom.

So, the reason why Qing was so good at pretending to be sick was probably because it was a skill he has been accustomed to since childhood.

Besides, Qing was confident.

To be exact, it's not a lie, right?

There was still quite a bit of debris left in the muscle.

All the large pieces were removed, and the remaining pieces were just grain-sized pieces.

However, because the fragments were so small, the pain was also minor.

It's bearable, to the point where the muscles were just starting to ache from overwork, and since it's concentrated on the abdomen and thighs, it's even more bearable.

From my experience so far, if you leave it alone, it will be pushed out by the muscles and settle under the skin.

If you gently poke it and squeeze it out, it will come out, so I guess you could say the treatment was almost finished.

Anyway, were you a patient? Yes.

Is this a serious wound? If it weren't for the constitution of the blood poisoner, it would have caused an immediate immune response, leading to high fever and necrosis of muscle tissue. Yes.

So, were you sick?

Hmm. Not that it's uncomfortable, but yeah.

So, Qing confidently pretends to be sick.

Because I have the right to pretend to be sick.

Because he was actually a sick person.

And so, Qing, who had finally finished preparing for sortie, moved forward, sobbing and groaning for no reason.

Even before entering the guest room, he staggered and pretended to be dizzy, and it was a complete feint even though no one was watching.

So, the bell reached the guest room and knocked on the door of the VIP room.

If you were from the Qing Dynasty, you might wonder what kind of people eunuchs are.

A group of powerful people, isn't that strange?

If we were to borrow a concept familiar from the Qing dynasty, eunuchs were the imperial housekeepers.

The eunuchs were organized into twenty-four organizations, called the twenty-four departments, and this was clear just by looking at the duties assigned to each of these organizations.

Palace maintenance and repair department, furniture manufacturing department, daily necessities manufacturing department, imperial clothing manufacturing department, imperial underwear manufacturing department (which exists separately), dyeing department for these products, imperial toilet paper manufacturing(!) department, pet care team, meal preparation team, palace cleaning (inner palace), palace cleaning (outer palace), heating and cooling management team, background music band… …etc.

Looking at it this way, what kind of existence would a eunuch be to the royal family?

They were the servants we see every day, the guardians who have looked after us since we were young, and the most comfortable friends we can only hope for.

So, the power of the eunuch comes directly from the favor of the imperial family.

And here.

The Byeongpil Sudang Eunuch was one of the highest-ranking eunuchs, with about six eunuchs under the chief eunuch to act as his proxy and assist him in his duties.

Since the power of the crown comes from the favor of the imperial family, the higher the eunuch, the closer he was to the imperial family.

The sound of a knock on the door.

Wibasun raises his head and smiles.

Because a smile was a basic quality of a eunuch.

But I thought to myself,

He obviously won't follow along obediently, so I'm thinking he'll probably pretend to be sick, let's see how long he can fake it.

In fact, malingering was an all too common tactic.

No matter how talented Sima Chunfeng was in the world and how powerful her wisdom is, she was no match for an old eunuch who has lived his entire life with political schemes.

On the one hand, you can look forward to it a little.

I wish there were new and innovative ways to do this, rather than using the common methods of feigning illness, pretending to be sick or paying for a parent's funeral, or using the family business as an excuse.

And then, with a creak, the door opens.

Gain's face reflected in the light illuminating the room.

Slightly furrowed eyebrows, weakly open eyes, and a pale complexion.

Although she was tall and has a manly appearance for a woman, there was something about her gait that was unsteady and disappointing.

Is Mac just missing?

The speed at which it was approaching was so fast that it was hard to watch, like a turtle emerging from land.

He made it seem as if he was pleading with his whole body and every action that he took, and finally he spoke with his pale face and prominent red lips.

'Upper line, I'm sick.'

Wibaseon pretends to be angry.

"Oh, you seem quite unwell. What the hell. Who were these Crown Princes, that they dare to cause such a disease in such a noble body? I will exterminate all of these bastards and hang them in the grave."

'Huh? No? There's no need to go that far. It's just a simple croak, hmm, maybe a simple horn… …?'

"Didn't the stone gods not light the fire last night? Didn't the previous ones neglect the cleaning, and that's why you're sick?"

'No, it could just be because I'm tired… … '

'Just leave these bastards here, Princess. I'll cut off their balls and offer them to you right now before the fever cools down.'

"Oh dear, then, I should just blow off the top of your head, right? I told you I'm sick. I have a fever, my whole body aches, and I'm coughing, coughing. Look, it hurts."

"Please keep the heat up. Then I can have a nice drink, have a cup of Yongjeong, and take a nap before I come back."

"Excuse me? Above, Sangseon? I'm talking to you. Hey, where were you looking when you talk? Can you see me now?"

The woman raises her palm and waves it in front of Wibasun's eyes.

Wibasun pretends not to know.

Whenever I go to see the Emperor, he always feigns illness and acts like this, so I suggest you cheer up a little, even if it's just a joke.

``Sir? Excuse me?''

``Yes, yes. It’s the upper line. You can’t call me that.''

Wibasun suddenly stops talking.

Because the white palm that had been waving in front of him was withdrawn, and the unfamiliar gaze of the stranger came to him.

Wibasun's eyes trembled slightly.

There was once a princess who was loved by all the eunuchs.

Yeonsul. The royal family's bratty tomboy.

Aside from her overgrown body from a young age, she was a princess who had no feminine features at all.

The royal troublemaker who laughed heartily and ran around like a little boy.

But he has a bright, smiling face that doesn't hate people, easily gives his heart and showers them with affection, and often acts childish.

So, among the eunuchs and female concubines in the palace, there was not one who did not cherish her like a daughter.

Of course, that magic princess was alive and well.

But even if a person doesn't die, or was alive, they can still lose something, so you could say that after suffering from a serious illness, a person changes.

Well, it's not surprising that such a beautiful princess has a scarred face and her memories were not intact.

But this woman, what the heck.

I lost my mind and became obsessed with the past. Would this be the case if the princess, who had grown up only physically since childhood, had not suffered from a high fever?

It's not just because they look similar.

The eyebrows that were frowning as if they were in pain, the eyes that were blankly unfocused for no reason, the corners of the lips that were subtly curved into a smile even in the midst of the pain, they were looking at me with that same expression that I had become accustomed to before.

``Were you a senior citizen?''

``Sangseon was not a name, ahem. Heavenly Blossom Sword?''

``Yes, I am not very good, but you were calling me with such kind words. Cough.''

Even the sound of that fake cough has become familiar, and I can't help but feel a surge of joy.

"Oh. Are you suffering from a cold or something? Now that I look at you, your complexion doesn't look too good. It's been so bad lately, isn't it?"

``It wasn’t a horn… I got poisoned in the fight with the White Hand Witch, so, ah, you don’t know what minority poison is, but it was really bad-''

``I know that too.''

The above-mentioned man cuts off his words with a stern expression.

Because I suddenly felt like I had been splashed with cold water.

The Heavenly Sword was the Heavenly Sword, and was the ultimate martial artist.

How could a masterful warrior be created overnight, or after years of training? From a young age, he must have cultivated his body with various elixirs and Dafa, and likewise, never let go of his sword, constantly striving through rigorous training. To achieve such supreme mastery at such a young age would have been necessary.

So, it may just be a coincidence that they were very similar, or that women with a cheerful and talkative disposition were usually similar.

Now that I'm calm, well, it's a minority?

``It’s a big deal for a small number of people, isn’t it?''

"Yes. I'm holding back, but it's not working. If you'd allow it, I'd like to return to the palace in better health. How can I…"

Qing slowly gets to the point.

I'm really sick. Can I go after I get better?

"Oh. I've already heard the tale of the heroic youth who defeated the White Hand Witch, so I brought some elixirs to help with the internal injuries. Would it be alright if I took your pulse to prescribe the correct treatment?"

I had anticipated this excuse a long time ago.

If you want to fake an illness, what better material was there than a few poisons?

If it hits and penetrates, it will destroy the energy pulse from the lower abdomen with extreme cold, so wouldn't it be better to use the excuse of recovering to buy time?

``Oh. Uh. You practice medicine a bit…?''

"I don't have the talent to call it medicine. The true masters were in the palace. If you find my skills lacking, why not try entering the palace and receiving a prescription from the royal physician?"

So, that's what it meant.

We all know it's just malingering.

If you don't want to get caught for no reason, just follow along. If you just say you're going, I won't bother to question whether you're faking it or not.

Hey, Miss Qing, this kid was a nobody.

In the case of a man who was usually unmanned, the temples were bulging, and the yang energy was abundant, so there was a certain aura that can be felt subtly.

But perhaps because he was a strong eunuch, his solar plexus was bland, and rather than showing any spirit, he had the strange cowardice typical of eunuchs. I was completely fooled.

But, isn't he acting strangely friendly?

Is it because of my mood?

Byung… … He’s smiling so openly, as if he knows it’s all just a faking illness, but he’s just going to wait and see what happens.

Qing, on the other hand, cautiously extends her wrist.

``I know it’s shameless, but I’d like to ask you to give me some elixir, since you were worried about my deep internal injuries…''

At that, Wibasun's eyes narrow.

Did you really end up being a victim of a minor illness, not just pretending to be sick?

Or was it that since he heard that he was going to take her anyway, he should at least get some elixir, and was he asking her to give him the elixir with an iron face?

Wibasun takes the pulse of Qing's wrist.

A faint ray of energy traveled through the veins, groping its way inside, and then…

``What the heck? How, how are you sitting there all right now?''

``Eunuch Wi, who is in charge of state affairs, has come, so I cannot welcome you while lying down……''

Wibasun was surprised.

It was so cold that it was freezing, to the point where even the expression ``frozen'' was too weak.

I heard that Soo-Han-Dok was notorious, but was it really this bad?

I wonder if even the ice crystals of the North Sea, said to be the coldest crystals in the world, could be this terribly cold.

Because that ice was right.

Qing had mastered the Ice White God technique and had already formed an ice crystal within his dantian. He simply released his true energy to his heart's content and tightly blocked the area around his dantian.

If a stranger were to feel your pulse, you would feel a terrible, unprecedented coldness, as if your lower abdomen were gradually freezing to the ground.

``Despite my shame, I have to see the Emperor in such detail. Where could such disloyalty lie…?''

Qing says this and opens her hand.

The meaning was clear.

Don't bet unless you're sure. Didn't you learn that? What were you doing, not giving me your elixir?

Wibaseon swallowed a curse inwardly.

Damn it, if that was the case, then why even bother summoning the Heavenly Sword?

It looks like it would die on its own even if left alone, but I wonder if they called it in for no reason and took out an elixir, and later even made it get a prescription from the royal physician.