\chapter{Journey to Beijing (2)}

Of course it rains in summer.

At some point, a damp, musty, musty smell began to rise in the Department of State Affairs building, and now it seemed as if the smell of half-dried laundry had inevitably accumulated in the humid space.

Well, the academic schedule at the Yizheng Martial Study Hall doesn't get cancelled just because it rains.

Would a drone avoid something as simple as summer rain?

Rather, isn't it a cool and nice bar?

Besides, when it rains, the unmanned vehicle doesn't fold its sword and quietly stay put to rest.

Whether it's snowing, raining, or a storm raging, you have to fight and win to survive, so we also do rain combat training.

As a result, even if you have two extra sets of clothes, they won't dry even after two days on a humid summer day.

The musty smell of poorly dried clothes somehow has something to do with poverty.

So, the first impression of Kang Cheom-ryang, the guest who entered the Yizheng Martial Study Hall, the first impression that seeped deep into the lungs through the nose with the first smell, could not be anything other than that.

Moreover, the soldiers of the Royal Academy of Military Affairs who stopped in bewilderment at the sight of the golden palanquin and asked, ``What on earth was that?'' were also equally shabby.

Isn't that what rain was like?

Because once you get completely soaked, whether you're a person or an animal, there's something about you that makes you look very pathetic.

"Anyway, how could it be so shabby and unsightly? Hey, look here, you. This was the State Council Academy. Would you just stand there blankly, staring blankly, even if someone of your stature were to raise a hand?"

Only then do the warriors suddenly come to their senses.

You might say that I'm getting too caught up in the topic of security guards, but that doesn't mean the guards feel a little wronged.

The doors of the Legislative and Military Academy were always wide open.

This was a declaration of the will of the Yijeongmuhakwon to accept anyone with a spirit of chivalry.

In addition, it was also a threat that if you want to quit along the way, you can leave at any time, that we will not hold you back, and that we have no regrets.

And there was no one else who would come all the way to the deep mountains.

And now, whoa! It's pouring rain.

In this situation, if you see a roofless palanquin, a golden palanquin at that, that has come in so naturally, it would be natural for anyone to rub their eyes, rub their face, and doubt their eyesight, wondering what on earth that was and whether they were seeing the real thing.

Honestly, it was a situation that would have made anyone feel dumb.

``Oh, yes, how did you come?''

``I am a widow.''

``Ah, wow… you were a great swordsman.''

Then the warriors look at each other.

Do you know someone called Wibaseon?

No, I don't know. Is he a high-ranking official?

Is there anyone in the world we don't know? Aren't they famous?

But if he was a strange figure riding in a golden palanquin, wouldn't he have been famous long ago?

Then perhaps the nickname would be something like Golden Palladium (the one who rides in a golden palanquin).

The two warriors were watching the situation closely, like guards, as they encountered an outsider who said, "Oh, it's me."

Then Wibaseon clicked his tongue.

``Even if you were a barbarian and a military man, how can you possibly know the names of high-ranking officials in charge of state affairs? I am a eunuch of Byeongpilsudang.''

You have to hear that.

Even if they were high-ranking officials, it was rare for them to know the local officials or central government officials who have immediate influence.

``Oh, Byungpilsu… Are you a eunuch?''

``But what’s going on here……''

The warriors' attitude became more awkward.

What about Byungpil? A high position? A man of great stature, riding in a golden palanquin, wouldn't he be quite a person of high standing? But why would such a man come here, drenched in this pouring rain?

Then, the eunuch Wibaseon, who was in charge of the military affairs, wiped the rainwater off his face and then smiled brightly and spoke.

``It was nothing other than that I have received the imperial edict from my office of royal secretariat.''

It was a single word that would make anyone come to their senses.

There were two types of words from the emperor: words from the officials were called edicts, and words from the common people were called imperial edicts.

If you combine the two, it will become the imperial edict, if you take them one by one, it will become the imperial edict, imperial edict, imperial edict.

That is, he came to deliver the Emperor's message.

Snap!

The warriors quickly kneel in the mud.

Wibaseon nods happily.

"Yes. Yes, that's right. Let's see. The Emperor wishes to convey a message to the Royal Academy of Political Affairs. Gather everyone immediately. Every single one of you."

The State Council was turned upside down because of the emperor's sudden decree.

The emperor's teachings cannot be questioned.

Even if it was a lie impersonated by someone, it was a sanctuary that cannot be doubted and should not be doubted.

Of course, if you forge the emperor's decree, all of your family members will not die a good death, so who in the world would dare to forge the decree?

This was not something that can be glossed over by hiding or running away, so even the most insane author would not dare to think of falsifying the school rules.

That was why, in response to the imperial edict that had appeared so unexpectedly, on this dark day in the pouring rain, every single person from the entire academy had gathered at the Great Training Ground without exception.

So, a kind-looking eunuch spreads out a royal edict under a huge umbrella.

``By the will of Heaven, the Emperor hereby decrees!''

At that moment, all the people rushed to throw themselves into the water.

Of course, the martial arts people were not particularly loyal people, so in reality, it was more of an inevitable hierarchy rather than respect.

So, even though I'm stuck in the mud and throwing my whole body into it, it's actually a bit annoying.

I don't have anything to wear tomorrow, I'm so pissed. No, if you really want to come, come when the weather was clear. But was it right to kneel here now? Etc.

-The Blood Cult has formed a group of evil spirits and has made enemies of all people, and has caused extreme harm from ancient times to the present.

-They murdered and devoured the people, and their only duty was hatred. No evil enemy in the past was as evil as the Blood Cult.

A voice filled with inner energy pierces through the raindrops and reaches my ears.

But what about the content? Suddenly, a blood cult here?

However, the order of the edicts was always like this.

Because it was written in the order of raising an issue – criticizing the issue – the emperor’s action – the emperor’s will.

This was the format used in the document room that manages the Emperor's documents, so the Emperor does not speak like this.

- While I was struggling with this, I heard the news of a loyal woman's victory over the leader of the Blood Cult. I, Ximencheong, a woman of the martial arts world, wishing to offer my sincere congratulations, entered the palace and accepted the Emperor's grace!

-This was my will and heart to never tolerate the evil that disturbs the country. Let the whole world know my heart through this!

If we were to remove the unnecessarily long and elaborate formulas and infer the emperor's words before writing them in the document room, it would be like this.

You said that Heavenly Blossom Sword defeated the White Hand Witch?

You were very kind! Come to the palace and I will give you a reward.

``Hurrah!!! Hurrah!!! Hurrah!!!''

``Long live the Emperor!!! Long live the Emperor!!!''

This was also the proper etiquette that followed the imperial edict, and it was the etiquette that the people should follow after hearing the emperor's jade sound.

But still, the sound was truly loud.

Instructor Ximen was receiving an award?

The Emperor himself will congratulate you? Oh my, was it true that even receiving congratulations was the best for Instructor Ximen!

This was surprising good news to the officials who had been called in wondering what on earth was going on, so of course they were shouting "Manse" at the top of their lungs.

However, it wasn't very pleasant for the person involved.

Before meeting the emperor's envoy, Qing visited Sima Chunfeng under the pretext of tidying up his clothes.

I'd like to hear some opinions from smart people.

"Oh, I've been hit hard. What should I do about this…"

Sima Chunfeng sighs.

"Heavenly Blossom Sword, this incident was clearly the fault of Bone Sima Lang. I offer my sincere apologies. It seems the palace was in a state of extreme turmoil. Bone Sima Lang should have anticipated this would happen…"

Sima Chunfeng bows his head deeply.

Of course, it wasn't something that Sima Chunfeng had to apologize for.

Who in the world would have expected something like this?

Originally, the emperor's teachings were not simple enough for a few people to come in and read.

Since it was a procession to honor the highest rank of messenger, it was normal for it to be accompanied by at least a dozen attendants and a spirited escort, forming a large group.

However, since it was delivered immediately in just one golden palanquin, it was intended to rush in without giving the palace time to think about anything else, that is, to summon them with great determination.

Sima Chunfeng explains to Qing, who was making that expression, that expression of, "Is this really such a big deal?"

The officials of the Department of Political Science knew that Heavenly Blossom Sword had defeated the witch and was injured in the process?

The world didn't know, because the official announcement of the Wulin Alliance never mentioned anything about the Cheonhwa Sword.

If such an announcement were made, the Blood Cult might rush in for revenge, and wouldn't it be difficult if the reputation of the Qing Dynasty spread even further, as they couldn't call Hwagyeong Hwagyeong?

I intentionally omitted such mentions to protect the Qing, so how did you know and single out the Qing?

So, the palace was being stubborn.

Since you mentioned Ximencheong so specifically, shouldn't you somehow be able to enter the palace?

It's a misunderstanding. Even if it's not me, I should have gone to the palace and told them first. I can't be so arrogant as to say, "That's not it, so I can't go," right?

Qing tilted her head at him.

``Hmm, was that it?''

"Heavenly Blossom Sword, this was no ordinary thing. To try to summon it with such force—"

``Hey, it’s not like there’s anything big that can happen if I call you anyway, right? It’s not like I’m going to find fault with you and kill you.''

If you call someone and behead them to congratulate them, who in the world would want to receive congratulations?

In fact, there were such precedents in the history of the Zhongyuan, but they were also criticized for being despicable acts for generations.

Because it was absolutely not something that can be done in the name of the Emperor.

"Oh, Heavenly Blossom Sword. They're clearly planning to keep you in the palace by giving you a position. Do you realize that palace officials can't leave Beijing without permission?"

``Well, whatever. Can’t it work out somehow?''

In fact, Qing has some beliefs.

Since the Empress was there, I can ask her to stop anything that seems to be going wrong.

- I thought about that and then suddenly.

But will the Empress help me?

My daughter who ran away from home has returned to my arms, so I asked her to help me leave home again.

Rather, what if you come forward and say that it turned out well, or declare that you were my daughter at Ximencheong and act like a princess that was not in your destiny?

Only then does Qing's expression become serious.

Will you help me…?

Sima Chunfeng sighed deeply at that.

``Heavenly Blossom Sword, Heavenly Blossom Sword, you should consider it a blessing, the greatest fortune bestowed by heaven, to have a close friend, a close friend, a close friend, with the greatest wisdom in the world, like Sima-lang.''

Sima Chunfeng said with the tips of his ears slightly red.

It's not known when they became close friends, but it seems like Chunfeng felt a deeper friendship than he thought.

"Ahem, Heavenly Blossom Sword will now be in critical condition. Luckily, I have a good excuse: if you say you're in critical condition due to the witch's poison, you can be relieved of your official duties."

Oh, indeed.

Qing nodded.

Even in history books, countless talented people pretended to be ill and stayed in the mountains and fields, because the best way to avoid official positions was to feign illness.

And on top of that, you're pretending to be sick?

Qing-i smiles, revealing her teeth.

A patient? That's my specialty, then.