\chapter{Journey to Beijing (5)}

The summer wind in Hanam blows from the southeast to the northwest.

The exact expression was southeast wind.

What this means was that the wind blows from the bottom of the mountain up to the highlands in the west of the central plains.

That is, those who come down from the mountain face a strong headwind.

And what if raindrops were carried by that headwind?

Rain falls horizontally, not vertically.

The expression on Qing's face as he sat in the golden palanquin was rather calm and peaceful.

Like a beast called a fox in the hometown of Qing, with a wise expression like a great monk who has forgotten the troubles of life and reached the five skandhas.

If I had to say, it's a drenched fox.

Qing calmly wipes her face.

She brushed her bangs, which were stuck together like seaweed, to the side, revealing her neat forehead.

Oh, it's cold.

This really seems like a real deal.

If the rain was falling sideways, or more precisely, from front to back, what's the point of holding an umbrella over you?

But it's a bit ambiguous to express dissatisfaction about it, since I'm not the only one getting rained on.

Not only the men holding each other's shoulders in front and behind, but even the eunuch holding a huge umbrella and tilting it towards the blue side seemed to have already gone into the water and come out.

Even the huge umbrella was swaying and shaking in the strong wind, so much so that it seemed as if the old man was somehow holding on in this wind and rain despite his strength.

Qing wipes his face again and looks at the backs of the cartmen.

But, this was because they were all martial artists.

The footsteps of the cartmen going down the mountain path were extremely urgent.

Just because they were palanquin bearers, they had no desire to carry their palanquins in the pouring rain. They were running down the hill, as if expressing their desire to get down to the village and rest.

But how easy would it be for four people to hurry together while maintaining the balance of the palanquin on a rainy mountain road, on a muddy and slippery mud?

Well, at least first class or higher?

He may be a first-class palanquin craftsman who was accustomed to pulling palanquins.

Or, it was the starting point of unmanned combat and a level that fits the description of a low level, the very pinnacle of martial arts that unmanned combatants display with their peak skills.

However, it was unlikely that a first-class warrior would continue to use him to the point of becoming a master of magic.

I guess we should consider them as the lowest level of the lowest level?

That old eunuch will be at least at that level, right?

They say it's an escort, but in reality it's more like a prisoner's escort or transport.

The situation of being called to the palace out of the blue was extremely suspicious in itself. Why would the Emperor come out and congratulate you for not only defeating a few witches, but also simply repelling them?

There's definitely some ulterior motive.

That would definitely be an unpleasant kind of thing.

Qing's usual behavior was to first check the escape route and then calculate the angle of escape.

However, it was not possible to see the escape angle all day, and the Uijeongmuhakkan was located in the mountains, more than two hours away even with the Qing's light attack.

They say that the hardest thing for people to endure was boredom.

I can't even stare blankly while getting drenched in the rain. It's such a long time, the day was so long. The clouds were blocking the sun, so I can't even tell what time it is.

What kind of joy must Qing have felt when, while sitting quietly in the palanquin during such an endlessly painful time, he caught sight of a house at the foot of the mountain in the distance?

And on top of that, when you finally leave the mountain path and the view opens up, wouldn't a golden carriage be waiting at the flat mountainside?

A dazzling smile appears on Qing's face for the first time today.

A golden palanquin, a golden carriage. Both made of gold, so where else but the imperial palace could these luxurious objects come from?

It was Qing who truly felt the importance of the roof.

Even though she had shown outstanding skills as a beggar who used the ground as her bed and the sky as her blanket,

Even if he was a gentleman, he wouldn't lie outside in the pouring rain. He should have taken shelter under a tree or a bridge. What kind of fool would lie down on the street in the pouring rain?

By the way, there was one such person among Qing's friends, but anyway.

``Sir, were we going to change to a carriage now?''

``So, did you know you’d be riding a palanquin to Beijing? Under the shade of an old man?''

He's so excited.

There were always people who say things like this.

If you ask, just say yes or no.

For example, if you put a table and say, "Wow, can I eat this?", then you're going to eat the food instead of just looking at it. Those were the kinds of people who make things difficult.

Of course, the old man wasn't like that from the beginning, so he might still be upset about the elixir being stolen, or he might be hurt because he had to hold the umbrella for a kid who was old enough to be his granddaughter.

What can I do? I have to endure it.

"at las……!"

It was a long time of humiliation.

From now on, you can sleep, eat, sleep, eat, sleep, and live comfortably in a covered carriage.

And isn't eating and drinking both of them the specialty that Qing was most confident in?

Qing's body shakes.

``Oh, Heavenly Sword. Will you stay still?''

``I’m sorry, but I feel like I’m getting chilled by the cold rain. I know it’s shameless to ask, but could you please go in first and warm up a bit?''

``Going in? Where were you talking about?''

He asks back, as if to say, "What does the above line mean?"

``A carriage? A golden carriage?''

"Oh, Heavenly Blossom Sword. How can you invite the young hero summoned by the Emperor to such a shabby place? Heavenly Blossom Sword's place was not within that place."

The old eunuch smiles sinisterly.

Feeling a sense of foreboding creeping up on him, it was at that moment that Qing quietly raised his eyebrows, wondering what this old man was going to do next.

Suddenly, a golden palanquin was lifted high.

This was because the palanquin bearers suddenly raised both hands as if they were standing in a state of punishment and raised the height of the palanquin.

The golden carriage approaching that state.

Suddenly, four men carrying palanquins jumped up, and thud!

The golden palanquin takes its place with a rough crash over the golden chariot.

``Oh, no way, this was my seat…….''

``Yes, it was a position befitting a hero who deserves the world’s admiration.''

Qing's expression becomes distorted as if he has chewed something.

In the meantime, the four legs of the palanquin were removed, and something was being tapped to drive in a wedge or something.

Originally, it was created to allow the combination of two golden palanquins and a golden carriage.

Then, they attach the legs of the removed palanquin to the window frame, hang a huge tent, and erect it vertically high.

Then four huge letters stand up.

"Young Hero Ximencheong"

"Buyi's House of Swordsmanship: A Discontented Look at the Sword"

「All the world was invincible and Buddha was invincible.」

"Calling to ascend to the level of the Son of Heaven"

Ximencheong, the hero of the millennium.

Because I was brave and took up my sword against injustice.

There was no defeat against any enemy in the world.

He was called to ascend the steps of the emperor.

The four of them sat side by side in front of the carriage, holding grand letters embroidered in gold thread on a thick red tent.

And then a series of people rushed in as if they had been waiting.

A drummer carrying a drum and musicians holding long flutes.

Soldiers wearing uniforms and carrying swords.

So, nearly a hundred people took their places around the golden chariot, proudly displaying their military standards.

Hmm, well, yeah, I think I get the point.

Even at places like amusement parks, when the parade begins, the highlight of the event, costumed actors take their places on shiny carriages and start dancing, singing, and waving.

That's exactly what it was like right now.

Since he was a hero summoned by the emperor himself, how could he save face if his path was ordinary?

They beat the drums and blow the flutes to raise the sound, and raised the flags to show off their majesty as such a great hero passed by.

Sitting in the center of a crowd of nearly a hundred, on top of a golden carriage, waving his hand solemnly, that's probably it…

But, in this weather?

Qing's expression gradually becomes more and more rotten.

In fact, for the emperor's edict to be carried out, at least fifty soldiers must form an escort.

So, the procession of the Cheonhwa Sword to the Imperial Palace was not that large in scale.

But so far, only a small number of people have come to the State Council and pretended not to know, so if I tell them in advance and give them time, they'll come up with all sorts of excuses and refuse.

Moving stealthily and quickly, I plan to lure out the Heavenly Blossom Sword first.

And once you put it in the palanquin?

From then on, making it known to the world became a shackle.

The Emperor has praised me so highly, so I cannot change my words. Even if I run away, the whole world will be suspicious and watchful.

So, he plans to advertise with great viciousness that Heavenly Blossom Sword was now on his way to see the Emperor and was entering the palace.

But, what about the weather conditions…?

Originally, there were immutable human attributes in the world that never changed.

That's war!

War, war never changes.

And also civil servants!

Civil servants, civil servants never change.

No matter what the situation, if I just do as I'm told and stay quiet, I won't get scolded. I just did what I was told, so it's not my fault.

If you act on your own judgment and adapt to the situation and something goes wrong, who will be held responsible?

That was why the gardener would come out with a watering can in the pouring rain and water the plants that were soaking in the rain, and why the guards of the Cheonhwa Sword would escort the Cheonhwa Sword in an open cauldron in the pouring rain.

Anyway, we're doing what we're told.

Just like this.

"The young hero Ximencheong was on his way to Beijing! Ximencheong, having defeated the Blood Cult's White Hand Witches, was heading to the Emperor!"

A mighty cry of a strong man piercing through the rain.

The flute blows the ceremonial music of the Zhongyuan, and the drums thump thump thump, a powerful sound that awakens the heart, assisting the march.

And the soldiers scattered coins in all directions, the famous Cheon Eun-jeon, the Emperor's grace.

A Cheoneunjeon was a small coin engraved with the words "Manse" (longevity). If you bring it to a government office, you will receive a favor equivalent to one doe of rice.

So, now that we were scattering the silver coins, it was literally pouring down rain and rice from the sky.

This was also the reason why the streets were bustling with people even in this dirty, bad weather.

And what a sight it was to see the young hero sitting proudly atop a gleaming golden chariot, even in the gloomy weather, before the gaze of countless innocent people!

Water was an efficient substance that always flows the shortest path, and the shape of the water path on the face was very pretty, like a reef that rises up beautifully, flowing down to the left and right of the nose.

The hair followed the flow, and the bangs covered the face like seaweed stems, leaving only the bridge of the nose, which split down the middle, standing out white.

It's a strange sight, with only the lower body exposed, but how beautiful and smooth that lower body is.

He was literally like a ghost of a noble family.

Moreover, although he was wearing a gorgeous enemy uniform, he was soaked in rainwater and his amazing posture, wow, really, what was that, the fierce lines that left me speechless were clearly visible.

The rain was pouring down and the sky was dark, but a ghost of a peerless beauty with her enchanting body clearly visible was sitting on a golden chair on a golden carriage.

Behind him, an old man wearing a hat and official attire holds a small parasol.

It does not serve any purpose in blocking raindrops at all, and was merely a decoration that should naturally be attached to an outing of a woman of high status.

"Heavenly Blossom Sword. Please smile a little. Wave your hand a little. And please, could you please put your bangs back? Why are you not showing that beautiful face?"

``It’ll fall again soon anyway. You want me to smile like this now?''

``Ahem.''

``Is this even okay?''

``How could I have known that it would rain like this?''

This was the result of bureaucracy.

The Imperial Palace had its own plans, and it only wanted to send a golden palanquin to honor Heavenly Flower Sword.

If you invited a guest and insulted them, the host's reputation would be in tatters. So there was absolutely no intention to insult or humiliate Heavenly Blossom Sword.

But what could he do when it rained like this?

Unlike Qing's homeland, the weather in Zhongyuan cannot be predicted in advance, so it was a realm of faith that must be left to the heavens through prayer.

Actually, even Wibasundo thought, 'This doesn't seem right. Is this right?' After all, he was a eunuch, a high-ranking official in the military, and he was supposed to be counting down the ranks. So, he was getting drenched in the cold rain and doing this.

Qing, what on earth am I doing?

If you ask whether you can see in front of you with your hair covering your eyes, in fact you can barely see.

But since it's a scenery that seems worth seeing, what on earth was going on?

Even in this time when the two, who have become wiser than anyone else, were gradually becoming wiser, the carriage still rolls on.

Towards Beijing. All the way.