\chapter{Journey to Beijing (6)}

The procession passes through Jeongju and enters Kaifeng.

The reason for passing through the Kaifeng openly was not only because the road to Kaifeng was well-connected, but also because it was a kind of provocation and mockery directed at the Wulin Alliance that had established itself there.

We're taking you to Ximen Qing, but you can't do anything about it, right? You just have to watch, right? This was the true power of the Imperial Palace. It's nothing special in the martial arts world, right?

So, the people of the Wulin Alliance also watched the procession at Ximen Hall with a complicated expression.

``The march of the young hero Ximen Qing!''

``The Emperor has bestowed great praise upon me, so Ximen Qing was going to Beijing to ascend the steps of the Emperor!''

This was the young hero, Seo Moon Qing.

It's not Heavenly Blossom Sword, it's Ximen Qing.

The intention was so transparent that everything can be seen through it.

Not a hero of the martial arts world, but a hero of the Zhongyuan.

I'm not talking about Heavenly Blossom Sword, but Ximen Qing himself.

Seeing the pitiful sight of Heavenly Blossom Sword sitting in the rain makes me even more upset.

And even in the midst of all that, seeing the familiar face of Alliance and the faint smile that spread across his face made me even more upset.

enN1WnIzcFhHMVJuR0JvdkNPc013eUtnR1NQRU5DemNLOFJRUW81aFpVbVFjRkZWcjhTNkk0QlRDR1o4a0hpaw

So the young hero's journey to Beijing passes through Kaifeng and crosses the river to Bokyang.

but.

Humans were animals that become indifferent to stimulation.

This humiliation, this shame that makes me kick the blankets and can't sleep, was displayed on the author's golden carriage, and it continues every day, so what was it?

All these escorts were beating drums and blowing flutes, shouting at the top of their lungs for the Youth Hero Ximen Qing, and even throwing money on the ground, saying that they would let me go.

It may be humiliating to my senses, but isn't it in fact a very honorable position for the people of Jungwon?

At first, I wondered why they were mobilizing so many people just to feed one person, Qingdo.

But even the old man who was ticking along was basically respectful and polite, and the soldiers and musicians who were escorting him were ready to kneel down just by making eye contact.

Of course, Qing doesn't know yet, but these were the Central Army, directly under the Emperor's command, and before they become the young hero Ximen Qing, they were carrying out the very precise mission of serving the one who will become the Crown Princess.

The Crown Princess was later framed and forced to live as a woman, either by giving up her military career or by forcing her to quit her military career. In any case, it was a scheme that meant the end of the military Ximen Qing.

But who would have expected that the Crown Princess would give up her position just to get rid of one person?

To use a metaphor like the hometown of Qing, it's like taking the opposing team's best prospect and paying him fifty times his annual salary, then leaving him on standby until he retires.

It was a very exquisite plan to take away the greatest divine being and the highest ranking person in the martial arts world, who was said to be the next best in the world, and to completely end the life of the martial artist.

The escorts don't know that far.

Just looking at her beauty, you can tell that she will be favored. Not just favored, but that she will eventually become a noble person like Empress Dowager Ximen. If she falls out of favor, she could end up ruining her family forever. Just meeting her eyes will make you tremble in embarrassment.

Qing was particularly weak to favors.

Being weak to kindness means being sensitive to kindness. Don't you understand this keynote?

I guess it was just bad weather, not meant to embarrass me.

Even now, if you look at it, they've prepared some emergency measures to keep warm, but, well, there's nothing you can do about the poor quality of the central region.

Primitive ancient hand warmers, such as an iron ball filled with charcoal wrapped in cloth, or a leather bag filled with hot water wrapped in cloth.

Actually, it wasn't cold even though it was raining a little, but it was still nice to have it on my lap and keep me warm.

So, Qing's attitude, which had been leaning on the golden throne without any motivation, gradually regains its vitality.

The fifth form of hair of the Ximen Surinryu.

Tie your bangs back, but don't let them all fall back, leaving a thin strand. When your face was wet, if it sticks to your face, you will captivate the world with the charm of a worldly witch.

Add to that a slightly frowning, awkward, ambiguous, and sad smile somewhere in between, and a sensuality that pierces the very center of the heart of the man from Jungwon blooms.

There, the world depicted by the silk clothes soaked in rain and clinging to the body was beautiful and intense!

So, the men who came out to pick up the silver coins in the rain were looking up at the carriage with their mouths open in a daze, with a hunched posture.

Even if a coin hits the forehead, the root just freezes like a wooden statue.

The men who were accompanied by their wives or lovers came to their senses after being harshly pinched, and were so distraught that they were unable to move their eyes in great regret.

Actually, women aren't that different, so, wow, a world of flowers! Is that a person, a person?

Because women also like beauty.

Even though it's summer, it doesn't rain all the time. If it doesn't rain, it's a real madhouse. If Qing raises his hand, everyone raises their voices. Heavenly Blossom Sword Young Hero Ximen Qing, and out of the blue, they shout "Long Live His Majesty the Emperor" and so on until their throats were sore.

As we enter Habuk in earnest, the rainy season has passed and even though it rains, the clouds were thin and the sun shines.

Qing's condition was excellent, receiving cheers in every city he visits, saying he was cool, pretty, and good.

There was also a food line, so I was invited to enjoy three delicious meals among those who were kind to me.

So, at first, Qingdo, who was a little cautious, gradually began to show her true colors, the terrifying behavior of a gluttonous woman.

White pork, boiled pork.

Here, white pork was a high-quality dish that has been prepared with all the effort put into trimming the tenderest part of the pork, removing all the tendons, fascia, small bones, and large fats.

And Qingjinrojagye, it's just Samgyetang.

However, since it doesn't contain glutinous rice, it feels a level lower than samgyetang.

And above all, when it comes to Habuk, it has to be Hwang Gwa-yeon!

A fantastic twenty-course meal made with Hwanggwa. For your information, Hwanggwa was also known as Oe and Oi.

A collection of twenty dishes made with cucumber.

Well, it's not that it doesn't taste good, but it doesn't feel like a meal without meat…

What should I say about Hebei cuisine? No matter who ranks it, it doesn't make it into the list of Zhongyuan cuisines. So, I guess it's understandable why they call this the representative of Hebei cuisine.

Oh, since there's no meat, no matter how much I eat, I don't feel like I've eaten anything…

``Heavenly Blossom Sword? How much do you want to eat?''

"But there's no meat? This bunch of grass, it's just a side dish after all."

The upper body was briefly stunned by him.

It's not only because it sounds absurd (to the Chinese, vegetables were the same food ingredient as meat), but also because there used to be a princess who said something similar.

They say that if there was no meat, it was not a meal, and if they only put grass on the table, do they think that I am some kind of animal that only eats grass, like a cow?

Although she looks like a cow, her eating habits have changed these days, and she was a princess who enjoys vegetables.

"Do you really need to overeat like this? You must be feeling unwell. You need to rest."

"Eunuch, shouldn't you eat well when you're sick? Don't you understand my heart's desire to force myself to eat in order to recover quickly, and my sincere desire to find healthy meat?"

He sees a bowl piled high with a line of wicker.

It's not just a bowl, it's a large cooking plate.

This was what the girl who was eating it with her eyes shining and saying it was so delicious said, so I was dumbfounded and speechless.

``What the hell was that, ahem, just a random word?''

"Oh, oh, oh. This was too much. What does Your Majesty think when you see someone who's in pain and pretends to be in pain? Even if they're in pain, if they try to show it, they'll probably be able to keep their composure. Don't you find it annoying that they insist on showing it?"

``What were you talking about all of a sudden?''

"But when you see someone gritted their teeth and pretended they weren't in pain, and silently endured their own suffering? Isn't that admirable?"

``Isn’t that the way the human heart works?''

"But was that how the world works? If a sick person tries hard to hide their pain, others will think they're fine and treat them as usual. So, the sick person will feel resentful and hateful, right?"

And then Qing-i Cheok points at me.

I'm sick, but I'm pretending I'm not.

But if you don't even know that and you're actually not sick, and you ask me why I'm eating so much, would I be upset? Or not? Are you really like that?

Wibasun shut his mouth tightly.

That damned tongue was so cunning, if you just listen to it, you'll find yourself thinking it's plausible, so it's best not to listen in the first place.

But, after listening to it, I ended up listening to it because it was fun.

``So, eunuch, could you please order two more dishes, both good for your health, with lots of meat? I’ll swallow them down and feel better.''

``No, I’ll eat more here, haa. Jeomsoi!''

In fact, in any situation, it was Qing who ended up getting along well and making small talk.

While Qing was enjoying his days like this, the procession continues to cross Habuk.

Now, with Beijing right in front of us.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Forbidden City, Geoncheonggung Palace.

This was the place where the Emperor's bedroom was located, and it was the most secretive and difficult-to-enter secret part of the palace, more so than any other secret place in the Zhongyuan.

Those who drink tea in the center of this Geoncheonggung Palace.

tap.

The Emperor's first companion, the Empress.

And the next generation's reserve emperor, the crown prince.

So, you might ask, what's so special about these three gathering around a tea table to drink tea? Even though they were emperors, isn't it just a cozy family time?

``Do you know the martial artist called Heavenly Blossom Sword?''

A ripple spreads through the Empress's teacup.

But was it normal for a court lady to have the ability to hide her true feelings?

He just took the teacup quietly and nonchalantly, so no one noticed the concentric circles inside.

I just quietly swallow my anxiety inside.

Why bring up the Heavenly Blossom Sword at this time? I still haven't found any evidence to expose the true identity of that wicked Heavenly Witch, the horrifying fake sorcery just thinking about it.

Outwardly calm, the prince answers politely when asked a question.

``I heard he was a commoner in the martial arts world.''

``You mean you heard it?''

``Isn’t the rumor so splendid?''

``Yeah. That’s right.''

The emperor said this and continued speaking as if he had just seen a dog passing by.

``Have a wedding with the Cheonhwa Sword.''

The prince paused at that.

What did you just say?

"your majesty?"

``You know that, I will give the status of lady to Heavenly Blossom Sword.''

That was when.

Hmph, the sound of breathing.

The Emperor's eyes twitched, the Crown Prince's eyes twitched, and the father and son's expressions were exactly the same, because they knew the loud noise that would come afterward.

``Your Majesty! That was not right!''

The Empress's voice was loud and clear.

``How can choosing the Crown Prince’s wife be so easy! To choose the Crown Prince’s wife, you must first conduct the Haeseon (first examination) to gather at least five thousand women. This was the proper procedure to examine the qualities of their parents, and also to determine whether there were any unrighteous ancestors or any illicit karma accumulated in their ancestors. After that, you must conduct the Choseon (second examination) to select four thousand women. This was to eliminate women who lack the righteous form and possess no evil deeds. This was a crucial process that will determine the form of the heavenly lineage that will continue for thousands of years to come, and to show off its majesty. Isn’t it the bare minimum to call together all the eunuchs of the palace and gather their judges to select four thousand women? And then, in the Bokseon (third examination), you must examine their bearing and tone of voice…

The expressions of the emperor and the crown prince were rotten.

After all, the proper selection process for a companion requires eight stages, including eight rounds of tests.

Surely you're not going to explain all of that?

And I (the child) know it all too!

But that suspicion turned out to be true.

These were the eight long-term selection strategies for concubines organized by the Emperor Taehwangjo.

The Empress let out a truly ear-piercing, angry voice, which was clearly a desperate attempt to calm her own startled heart.

What kind of nonsense was this!

The child born from my womb and the daughter born from my womb were getting married. There was no case in the world where even animals can be so attached. Isn't it so absurd and horrific that it makes me shudder to even mention it?

``Ahem, it’s not just a matter of selecting a lady, it’s not something that requires such a grand and thorough examination…''

``What the heck!? Now, as the crown prince’s companion, that kind of wife, that lowly woman, that street child, that woman who only uses people, a b*tch, a b*tch! A b*tch! What will become of the royal family’s protection!''

Even though the Empress stutters, it was truly difficult to curse her for the sake of her daughter.

From the perspective of the rich father and son listening, if the empress, who had never uttered a harsh word in her life, were to say such a vulgar thing, she must be really angry.

But the Emperor's will was firm.

``Ahem, Your Majesty, calm down. I have a purpose for this, and it was all for the greater good of peace in the world.''

``However, Your Majesty-''

``Ahem, yes, yes, you know that. The Crown Prince also knows that, so prepare to welcome the Cheonhwa Sword.''

``Yes, Your Majesty.''

The prince, a good listener, nods his head obediently.

So the Empress cried out again.

``Your Majesty!''

``Madam, calm down and we’ll talk later. For now, step back. You too, Crown Prince.''

The Empress's fist trembles.

That stubbornness, once he sets his mind to something, he has to do it even if the sky splits, so he meant that he would do it anyway.

After all, Geoncheonggung Palace was the emperor's residence.

Even if they were his wife and son, he has no choice but to go if they were told to go, so the two of them end up being kicked out of Geoncheonggung Palace together.

The Empress's residence was in Jangchun of the West Palace, and the Crown Prince's residence was in Dangyeong of the South Palace. The Crown Prince was bowing to his mother and was about to leave.

The Empress speaks with a stern expression.

``Prince, please come to Changchun Palace. I have something important to tell you.''