\chapter{Journey to Beijing (7)}

The purpose of the design of the Forbidden City was to 'kill energy'.

The south gate of the Forbidden City was located in the center of the fan-shaped wall in the shape of the Chinese character for "冂", a common design in defensive structures, and was effective in intercepting enemies attempting to break through the gate from three sides.

But what was outside the South Gate?

This was where Tiananmen, the first gate of the Forbidden City, was located, destined to be a place of eternal peace and immortality.

There were huge walls four meters high in front and on both sides, and behind them was the even taller gate of Tiananmen.

So, the moment you enter the South Gate, it becomes a completely closed space in the shape of the letter ``口'', and you cannot see the sky at all unless you raise your head all the way.

And what kind of emotions do people feel in such places?

I feel awe and fear.

``Oh, well done…….''

Of course, limited to people from the Zhongyuan.

The people of Qing's hometown have become accustomed to high-rise skyscrapers and enclosed spaces, so don't high-rise complexes actually put even more pressure on them?

So, Qingdo can only feel like a tourist destination.

Anyway, those Zhongyuan guys were said to have built a really cool wall.

Well, just look at the Great Wall of China. What kind of walls were they connecting like that?

For reference, the actual length of the Great Wall of China was about 54,000 li, so it should be called the 54,000-li Great Wall rather than the Great Wall of China.

The Great Wall of China was a symbolic number that represents the highest number in the Chinese calendar.

Visitors to the Forbidden City were basically required to wait in front of the South Gate for anywhere from an hour to three days.

The original purpose of the building was to kill the spirit.

Kneeling in front of the South Gate, how many arrows and cannons were aimed at him from all sides?

In this closed space where it feels like a rain of arrows might pour down at any moment, all you can do was wait for the door to open.

It was a series of horrific times that were truly blood-dry and heartbreaking, but that's their situation.

Qing sits on her knees and looks around.

Today was a rainy day, and despite the bad weather, soldiers stand densely on the walls, looking down on the city.

A woman wearing a cotton swab appears, kneeling down, and fearlessly turns her head here and there, watching intently.

Thanks to you, the soldiers were dying of curiosity.

If it's Ximen Qing, isn't it the Heavenly Blossom Sword, Samdugain, Odubangjeong, Hwajungcheonhwa, and the peerless beauty considered the best beauty in the world?

Wow, seriously, Samdu Gain, this was crazy. He's falling behind, wow. But I understand Samdu, but why Gain, please clear the slate so we can see his face too…

I heard that Qing has to use cotton thread from here.

Because it was the entrance of a woman who had been designated as the crown prince's lady.

When he was promoted as a young hero, he was widely known and promoted as a palace official.

Because after entering the palace, as the Crown Princess-to-be, she must not show her precious face carelessly.

Qing didn't know the reason, but she just wrote because she was told to. It was hot and it was a hassle to control her expression, so she thought it was good.

So about half and a half of that.

In this primitive age, when everything had to be built by hand, the high walls that boasted a solid status were impressive.

The sight of soldiers wearing armor and carrying red-clothed swords on the walls was also a sight to behold.

But, how long were you going to just watch?

``By the way, sir? When does the door open?''

The stomach was bursting.

There's a limit to being bold. How could you not be intimidated in such a dangerous place, and just sit there, turning your head slightly and watching?

``No, please. Please wait. Do you think the gates of the palace of the Emperor, where He resides, will suddenly swing open just because a guest has entered without a headdress?''

``No, I called you and you didn’t even open the door. How can you treat a guest like this…''

Wibaseon whispers in shock.

``No, please shut that damn mouth.''

``Did I say something wrong? If you invite a guest, the host will immediately open the door and welcome you!''

``Haaaaaaaaa!!!''

Wibasun screamed and covered Qing's mouth.

Even in the midst of all this, Heavenly Blossom Sword continues to speak with his lips trembling. Is he being bold or was he completely ignorant of the ways of the world?

So, sitting inside the Qing-i cotton swab with a serious expression on his face, the view was worth looking at, but it wouldn't be fun to keep looking at it while getting drenched in the rain, so what the hell was this nonsense that he called out to?

``Sir, was it okay for me to bow deeply instead of doing this?''

``……You’re not trying to sleep, were you?''

``Oh, no way. I just knelt because the Emperor called me here, but even keeping my back straight felt disrespectful.''

``You must not sleep.''

``I told you I’m not sleeping, haaaam.''

``No, you said that and then fell into a deep sleep.''

"No, sir, what? I never said anything like that. I did doze off in the palanquin a few times, but it was just because I had lunch in the sunlight for the first time in a while."

``No, definitely in front of the Queen’s Palace-''

Suddenly, Wibasun shut his mouth tightly.

Qing immediately bows down to him.

What's wrong with that? Strictly speaking, it makes no sense to summon someone and then force them to kneel before the gates.

Qing knelt down and bowed deeply. Ah, the stone floor was damp with water flowing down it, so it was a little, no, quite uncomfortable.

Qing relaxes his eyelids.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

``Your Majesty, I will open the door.''

``…….''

"……majesty?"

``Oh, yeah, open the door.''

The prince suddenly came to his senses and responded solemnly to the eunuch's words.

Wouldn't it be right for the prince to personally go out to greet her, as she was a woman who will one day be welcomed as a lady?

It was an order given directly by the Emperor, so the Crown Prince came out to the South Gate on a rainy day like this.

Guguguguuung-!

The south gate lets out a huge scream.

How could a huge gate, three slabs high, swing open silently and with a loud clang?

It was a huge structure that takes at least one arc (fifteen minutes) to open completely, as it does not move even if you pull the strings with all your might from both sides.

Behind him, the prince falls into thought again.

…

… …

… … …

``Your Majesty, do you truly intend to follow His Majesty’s reckless orders?''

``I'm embarrassed, too, but I'm just a lady. I didn't order you to get caught in the rain….''

The Crown Prince's Lady was at the very bottom of the line of government officials, that is, the youngest of the main wife.

This was a position that would later be promoted to a concubine when the emperor ascended to the throne, so in fact, among the women in the palace, these concubines were the most ambiguous.

Although the main wife was the main wife, she was too far from the main family to have much power, so most of the concubines were usually just a puppet for political purposes.

In severe cases, there must have been many cases where people grew old and died alone throughout their lives without ever seeing the Emperor's face.

Moreover, he was beaten by Jeonghu.

Because Bin was the perfect person to vent all the frustration that has built up in the fierce struggles of the palace.

And below, Seohu, beaten by concubines.

The emperor's concubines were often favored by the emperor, and these favored concubines held more power than the marquises and wives of the emperor.

It's so empty that it's almost like you can just crush it and there's still some left.

"No, that's not right. How could the crown prince, who will one day ascend to the throne, have such a, such, such a woman? Oh, how absurd. Even if she's a lady, it's not right. I, the mother, am against it. It's not right."

"But, Your Majesty, haven't you already made up your mind? No matter what I say, you won't easily change your mind…"

"But this time, the Crown Prince will have to oppose it. He's against taking in a concubine, and his mother will oppose it, too. And if he were to bring in such a woman, would the ministers, high and low, remain silent? If they all kneel and plead with one heart, the Emperor will surely step down this time."

Suddenly, a question occurred to the prince.

"You keep saying that kind of woman. If she's a lowly woman, she's a lowly woman. If she's a murderer in the martial arts world, she's a murderer in the martial arts world. Why can't you just keep talking about that part?"

"I'm sure Your Majesty has his own agenda. There's bound to be significant opposition from his subjects, so as a son, I'll intervene—"

"Oh my! Am I not a mother? The Emperor was the father, and I am a lowly servant! How can this child, whom I gave birth to with such great pain, be so, oh, oh, how can my life be so miserable? Where on earth was such a law? There was no such law in the world, no such law…"

It was the empress who shed tears no matter what.

The prince was greatly embarrassed.

``Mother, don’t be like that. If you hate that woman so much, I’ll have you locked in a corner of the West Palace warehouse so you won’t even see her.''

That was the time.

The Empress holds the Crown Prince's hand tightly.

Then, he stares at the prince with sad eyes, swallows hard, and opens his mouth with difficulty.

``Hoeyak-ah. That woman was Yeonsul, your younger sister, Princess Yeonsul.''

"yes?"

``Not the fake Yeonsul in the palace right now, that Heavenly Blossom Sword kid was the real Yeonsul, your younger brother Hal.''

Suddenly, the atmosphere was like a crazy love story!

The prince, upon hearing the surprising secret of his birth, immediately freezes.

Heavenly Blossom Sword was the princess of Yeonsul?

And the princess who was currently in the palace was a fake princess, and the most promising young talent who was a divine being in the martial arts world and the next best in the world was my younger brother, Sohal!

"Those wicked Indian sorceresses were the ones who switched things up. They took Yeonsul, saying they'd save her, but they left her to die. They brought in a substitute somewhere. How could Yeonsul not live and grow up so wonderfully? That alone was enough to give me thanks to heaven, but now you two were engaged? How could such a thing happen in this world?"

The prince's heart sank as he watched the empress speak while beating her chest.

My heart dropped and I felt dizzy.

Oh, how could this be, how could this be… …!

Madness!

My mother was crazy!

You're still so sane, how can you be so mad already? No way!

That's only natural for a prince.

If we were to substitute it with the expression of the hometown of Qing, anyone would be able to understand it.

A chaebol family, a chairman who encourages his children to get married.

eS82cEF3M2JnbHlDcjVodFVtUDBmNVhxbmlRVm1sVm5XMFV6OGR3WnNpWUpEL1MvNm9HNnllaUo2bytTZ1h5ZA

His wife, who opposes him. "You must never follow me, and you must not let dirt get in my eyes. Step over your mother's corpse and go!" "Just step over your mother's corpse and go forward!"

And the shocking truth was revealed!

The truth is, the cleaning lady just switched places, and that woman (the best actress in the country, she's pretty) was your real sister!

The younger sibling I have now was fake!

If Heavenly Blossom Sword had truly been a nameless, unknown martial artist, it might have been a bit more convincing.

But, the famous young master who was the best martial artist in the world and also the next best in the world was suddenly called the princess of Yeonsul?

``Mother, please, as I told you before, Yeonsul was in the palace. My younger sister, your daughter, Sohal, was doing well, right?''

Besides, it wasn't even his first offense.

Wasn't it your mother who had always thought that Yeon-sul was strange, that she couldn't possibly be your daughter, and cherished her, wrapping her in the hem of her skirt, but after she recovered from her serious illness, she neglected her and didn't visit her even once?

Even if I brought Yeonsul to see her, the empress would turn her head away and pretend not to see me.

However, recently, he has become much more cheerful, and I thought he had gotten better because he was eating with me and receiving greetings.

"That woman was a fake, Hoeyak, think about it. No matter how many times someone dies or comes back to life, how can they change so much? What kind of sorcery do you know? Even you've seen strange women pretending to be sorcerers, haven't you?"

``Well, it’s because I don’t remember, isn’t it? Please, Mother, oh, Mother……''

The prince's eyes were red.

Okay, I understand for now.

The prince's heart was truly heartbreaking as he said, "I understand," and then withdrew, trying to comfort his mother, who was crying in sorrow.

What on earth was this?

My younger brother's delusions were strange, and my mother can't seem to get out of these delusions either. It's truly strange.

How could such a terrible thing happen, when a father leaves his daughter behind and searches for her, only to find that the daughter was being treated coldly by her own mother?

Even the heavens were indifferent… … …

… … …

… …

…

The door opens and the prince walks out.

``Bring His Highness the Crown Prince!!!''

The prince's eyebrows arched and pressed against the center of his eyes.

What was this? Something very, very familiar, with a plump figure with his head bowed to the ground, and a very, very familiar crown?

The eunuch Byeongpilsudang pokes him in the side with his scepter (a slightly curved stick of unknown purpose carried by officials).

Then, like a cat that had been splashed with water, the woman bounced her body up.

In that frost, a cotton thread with beads strung on it hung overhead, the drenched cotton thread flipped over in a very pleasant trajectory, and with a snap! it stuck to the woman's crown.

The face of the frosty woman was clearly revealed-

At that moment, the prince gasps and takes a deep breath.

Regardless, the woman blinks her big eyes, then gasps and wipes her mouth with her sleeve.

A woman bows deeply again. However, it was a man's deep bow.

When the eunuch Byeongpilsudang poked his side again, he made a ``ah'' sound and this time bowed like a woman.

``Ugh!? Hot, ah, Your Majesty? I see you, Your Majesty.''

The prince's eyes shook without mercy.

What, what on earth were you talking about?

This, this utterly familiar, yet also so longed for, yet so pitiful a sight that it's hard to bear to look at?
