\chapter{We Are Looking For Someone (4)}
\textit{Anyway, tasting the gift on the spot, even though it may not be polite, would definitely create a very pleasing scene. Right?}

Qing put a leaf soaked in poppy sap into her mouth and chewed.

It was bitter at first, and then it had a rather strange taste.

Truly, an indescribable flavor and texture.

The pickled leaf didn't dissolve or break down in her mouth, but rather just oozed a bitter juice.

It wasn't bad enough to spit out, but it also wasn't all that tasty either.

But well, it wasn't meant to be eaten for it's flavor in the first place, so what else could really be done? All she could do was endure it.

How much time had passed since she thoroughly chewed and swallowed even the fibrous residue?

Soon, a drowsy medicinal effect spread throughout her.

It felt like she was somehow floating, making her feel at ease as if everything in the world was soft and fluffy.

After crawling on her butt until she reached the wall, Qing slumped down against it.

In truth, opium poppy was considered more of a first-aid medicine in Zhongyuan.

It was because of its excellent efficacy.

It reduced fever, relieved indigestion, and stopped diarrhea.

Moreover, it soothed pain and hunger, a truly miraculous herb like no other in Heaven and Earth.

On top of that, it was hardy and grew in abundance.

It was common practice in civilian households to grow a few of them in the backyard for medicinal use.

It was common for female martial artists to carry it around. After all, it helped alleviate the discomfort and agony they experienced in a certain few days of the month.

It wasn't just about feeling like shit and a bit nauseous; the merciless Jianghu did not consider a woman's circumstances. It was potentially more fatal than mere sickness.

As such, the other two did not really stop her.

Per usual, Changbin had something to say, but looked away awkwardly instead.

Meanwhile, Peng Daesan just gave a piece of advice.

"It is not healthy for a martial artist. It is best to use it one at a time only when absolutely necessary, but-"

Then, he looked towards Nan'gong Shencai.

Or at least, Peng Daesan believed he just looked at him.

"How do you know about that day of the month, Big Brother Nan'gong? And to think you would even keep track of such a thing. How is this so?"

"Huhhh. Little Brother Peng, your gaze is quite impolite, is it not? It was not me who kept track, nor am I the one to bring such a herb. Elder Keeper of Secrets gave it to me."

"Elder Keeper of Secrets, you say? How did such a figure?"

The Discipline Elder of the Beggars Union, Keeper of Secrets Lu Gu, was well-known for his obsession with secrets.

"When I first met Sword Friend, coincidentally, there was mmm...misconduct. Hmm. Yes. That happened. I thought, how could there be such a fierce woman in this world? Perhaps the Elder thought the same after seeing that situation and wished to give her some poppy."

"Ah."

The glint in Peng Daesans eyes changed.

Misconduct. And fierceness.

What exactly had the Keeper of Secrets seen to personally send poppy to a girl who could be his granddaughter?

"There is no need to send such pitying looks. Well, in the end, I became friends with such a precious Sword Friend. Is it not just like that saying? It is unpredictable how joy and misfortune would enter your life. Is that not so, Sword Brother?"

"Yeahhhhh. Sword Friendrrrr."

Qing raised her arm and slurred.

Poppy was originally a toxic plant.

Seeing how she took a huge bite from the start and thoroughly sucked out all the juice, it was no wonder she was intoxicated.

Normally, poppy was finely chopped or brewed like tea to control its effects.

Peng Daesan cocked his head.

\textit{What is this? Why is she acting like someone whos chewing on poppy for the first time?}

"Could it be? You..."

-Esteemed guests. Dinner has been prepared.

A servants call inviting the guests to dinner interrupted Peng Daesans words.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing wasn't drunk but rather, high on drugs.

Strictly speaking, alcohol was also a drug. As such, drugs had major categories, each with different effects.

Alcohol stirred the meridians, lifting spirits and leading to hasty decisions.

On the other hand, opium clouded the mind, providing a dreamlike comfort.

Qing was in a very, very comfortable state due to the drugs effect.

It was similar to how she felt when staying at the Divine Maiden Sect.

And at the Divine Maiden Sect, she always behaved in a fixed manner. After all, she had to always be wary of Ximen Surins nuclear noogie airstrikes, delivered from the medium of Sword Flight.

Originally, habits tended to surface more when the mind was muddled, so it was only natural for Qing, high on opium and delirious, to reveal her habits. 

A girl akin to a gentle butterfly meandered the path.

Peng Daesan frowned and Changbin glanced at Qing.

Nan'gong Shencai was originally indifferent.

Also, having already seen all sorts of sides from his Sword Friend, he didn't mind as long as it wasnt too unsightly.

Meanwhile, the Daijing Sect Leader Wang Gouru and his children rubbed their eyes.

\textit{Who is that? Is that the same thing as before?}

After all, she was the very woman who gorged herself earlier, as if the snacks were her parents murderer she wished to annihilate from the world.

And then, throughout the conversation, she showed signs of drowsiness. Didn't she even nod off a few times?

But now, she had suddenly appeared as a girl full of grace, so it was only natural for them to be so surprised.

Poppy made one forget hunger and provided a sense of fullness.

As such, unbecoming of her, Qing slowly picked out and savored only the delicious foods.

Among everyones astonishment, there was one person who felt a different, ticklish emotion.

It was Wang Gouru's second son, Wang Xunwan \footnote{灣 'bay tide'. Sonman in the original text}.

It was because of this guest who kept smiling and making eye contact with him throughout the meal.

{\itshape Has Young Lady Ximen taken a liking to me?

After all, the look in her eyes was too blatant to say it was not true.}

Sometimes, when their eyes didnt meet, he thought she might be focusing on something above his head for a moment, but soon she would meet his eyes again and send him a beautiful smile.

Pride surged from deep within Wang Xunwan,

{\itshape Thats right. It is me! Not Big Brother, but me! 

Its this Wang Xunwan who she is interested in! Not Big Brother, but me! Me, I tell you!}

Consequently, a gradually increasing sense of discomfort emanated from the Jade Qilin, who was sitting next to her.

Putting aside the anxious beating of his heart due to seemingly rubbing off on a Master the wrong way, Wang Xunwan's nose pridefully turned up and the angle of his jaw lifted.

\textit{The Jade Qilin is far too handsome, so she probably didn't even consider him in the first place, right? When thinking realistically, I, this Wang Xunwan, must be the most charming person here.}

Wang Xunwan was intoxicated with a sense of victory while Peng Daesan seemed increasingly uneasy for some reason.

Qing, however? She was just happy.

{\itshape This is what it means to be happy just by looking at something.

-324.

How could a number be so beautiful?

Whether the Mission Window considered the common folk as humans or not, that didn't matter for shit in this situation. That bastard was a martial artist, so he was definitely one shitty ass motherfucker.}

His father had Righteous Karma, his older brother had Righteous Karma, and even his sister, who kept giving displeased looks, was only -17.

So, it was quite curious and rather impressive that he alone seemed to scream 'I'm different!' by having over an Evil Karma value that was over three hundred.

And above all, she was so very grateful. She couldn't help but commend him from the depths of her heart.

His talent was confirmed at the afternoon tea she had earlier.

And after hearing the story about the missing cases in their room, the puzzle pieces seemed to fit perfectly.

{\itshape Ah. It's that motherfucker!

The reason for dragging the Daijing Sects name through the dirt?

Because obviously, it worked. It made it easier to fool ordinary people.

If it was said to be a lucrative task requested by the righteous, orthodox Daijing Sect, it would not seem all that dangerous at first glance. Furthermore, the fear of repercussions would have been lesser as well.

But in order to pull it off?

There had to be some kind of assurance that the request indeed came from the Daijing Sect.

Then, what if the second son himself was personally involved?

Wasn't it only natural for it to be believable at that point?

So, it was a kind of fraud. In modern terms, it was like handing over a fake business card to fool gullible people.

Huh, I guess all these scamming motherfuckers think the same way. How is it that they are all so identical?}

Qing thought, her mind soaring due to the drugs.

{\itshape What would it have been like in-game?

I probably wouldve had to lead some comrades, find evidence, search for people. Even witnesses may have been necessary. 

Maybe I would have dragged literally everyones name in the mud? You're the culprit! No, you! Nah, it's the father! No, the mother! Sorry, I meant the grandfather! Nevermind, it's the grandmother! I would have accused everyone, tarnishing their honor. I mean, as long as it's not me, right? Who cares about them NPCs?

After all, in games where attacking NPCs are not allowed, only after uncovering the conspiracy would they get judged as an enemy.

And then, I would be able to beat the shit out of them.

But right now?

Is this a game? To be honest, I don't really know either? I guess?

But does that mean I can't attack?

Nah. Fuck that.

Status Window? If you want to stop me, just try it.

Fuck it. I'll fuck over whoever I want. Of course, I mean metaphorically. My dick is gone, after all. Anyway, fuck off. I'm gonna do as I fucking please.

Even if my dick is gone physically, I believe that the cock and balls of the soul is what makes a true man!}

Qings smile grew increasingly similar.

Fortunately, a catastrophe where the girl, overflowing with Heavenly Slaughter, suddenly started emitting killing intent did not occur.

It was because the meal ended at just the right time. 

After they finished eating and got up to return to their rooms

Qing whispered to Wang Xunwan as she passed by him.

-Young Master, I will see you at the side gate after midnight. I will be waiting.

Steam seemed to snort out from Wang Xunwan's nose.     

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Even Qing couldn't help but doze off slightly due to the medicinal effect, thus being a bit late.

Of course, it wasn't Qings fault at all.

The responsibility for being late was entirely on those primitive Chinese of the Middle Ages who didn't even have a clock in their rooms.

Meanwhile, unbeknownst to Qing, there was more than just one side gate in the Daijing Sect.

So, Wang Xunwan paced back and forth near the sects side gates as the time approached, his heart burning with impatience.

\textit{Was she just playing around with me?}

Come to think of it, he thought there was no reason for her to choose him over the formidable members of the Heavenly Martial Team. Even in the slim case that she did, there was no reason to specifically flirt with the second son when there was a separate successor to the sect.

{\itshape But those eyes..

What if she was just briefly delayed because she dozed off?}

Thus, Wang Xunwan wandered for about an hour and a half. 

To put it in modern terms, he basically waited aimlessly for three hours in the hope of banging a girl. 

He was truly an exemplar in displaying the sorrow of a man.

And finally-

"Ah. Young Master. I apologize for being late."

"Not at all. Damsel. I have just arriv- Nono, I have waited a long.time, but it is no matter."

Wang Xunwan started with the usual stereotypical reply but then corrected himself, realizing the oddity in his words.

It wasn't right to say he had just arrived when it was more than an hour and a half after the expected time. Claiming he hadn't waited long would make him seem tardy, after all.

"Um, Young Master. I am embarrassed to ask this, but-"

"W-What is it?"

"Is there perhaps a place where one can scream loudly without being overheard?"

"Heuk."

Wang Xunwan spat out his last remaining breaths in spite of himself.