\chapter{We Are Looking For Someone (1)}

In the era when the Wulin Alliance did not exist, the Orthodox Faction were just loosely connected conglomerates of large sects and clans.

The important point was that they were connected, albeit loosely.

They maintained friendships by attending each other's family events or inquiring about each other's well-being through letters.

It was during this time that the Hidden Dragon Assembly was established.

Initially, it was not even a gathering of Rising Stars.

It was simply a group where the real authorities of the clans and sects got along and formed a sort of society for family events.

It was a gathering where they collected small amounts of money to contribute to each others celebrations, such as first birthdays, sixtieth birthdays, weddings, and funerals.

Then, the Demonic Cult attacked.

The Orthodox Faction had to unite their strength to survive.

But what had to be remembered was that everyone within the Hidden Dragon Assembly were practically neighbors.

Moreover, their connection to each other was similar to as follows. 

Our son is your son-in-law and your son is his son-in-law and his son is our son-in-law.

Thus, while shouting 'Are we not all family?', the united forces of the Orthodox Faction in Zhongyuan repelled the invasion of the Demonic Cult.

It was the birth of the Wulin Alliance.

After the alliance of the Orthodox Faction officially launched, the Hidden Dragon Assembly was transformed into a reserve combat team composed of young martial artists.

However, there was always a social hierarchy, even amongst such a supposedly close-knit alliance.

The noble youths of the Nine Sects One Union and the Ten Noble Clans could not possibly share the same table as the crude Orthodox Faction.

Therefore, the Hidden Dragon Assembly was divided into two groups.

The Heavenly Martial Team. And the Earthly Courage Team.

The Heavenly Martial Team consisted of youths from the Nine Sects One Union and the Ten Noble Clans, including special members who had received recommendations from more than 10 members of different affiliations.

The Earthly Courage Team gathered the rest of the youths.

Therefore, every young sprout of the Orthodox Faction dreamed of becoming a member of the Heavenly Martial Team.

To them, the members of the Heavenly Martial Team were the true powerhouses of Wulins Orthodox Faction, floating and playing above the clouds. 

Even after excluding materialistic factors, all the members were Masters far beyond their age group.

The true Hidden Dragons who achieved remarkable accomplishments!

As such, it was no wonder the youths of the Orthodox Faction aspired to join the Heavenly Martial Team.

In their imagination, the members of the Heavenly Martial Team spared no effort in elevating each others martial arts through earnest focus and practice.

Surely, they would generously share and debate the principles and logic of the martial studies they had realized.

'Ah! If only I could be there to join in their discussions and share my opinions!'

It was the dream of every young person in the Orthodox Faction.

And here in this place, Qing was enjoying that very dream.

It was a clear, pure, and meaningful debate on martial studies with members of the Heavenly Martial Team.

"Everyone in the world has stated that the order was Hundred Day Spear, Thousand Day Dao, and Ten Thousand Day Sword. Does this not prove that the sword is the King of All Weapons, thus showing its superiority over all armaments? What do you think, Sword Friend?"

"I agree. What about you, Daoist Changbin?"

The Mount Hua Sect was also known as the Mount Hua Sword Sect.    

Basically, it meant they were people who wielded swords.

"As a Plum Blossom Swordsman myself, I cannot help but acknowledge that..."

Qing nodded and declared.

"Then, by an overwhelming majority, the motion that the sword is far superior to the dao has passed."

Peng Daesan frowned.

Qing grinned and brought up the next topic.

"Then, for the next item on the agenda, I propose that since a dao is a sword that only has one edge, it should be considered half a sword. Shouldn't we start calling it a half-sword from now on? What do you think?"

"Ohh! Sword Friend, to think you came up with the word, half-sword. What a precise description of the dao. This is the first time I have heard such an accurate term in my life. In fact, it is even moving to hear such a word. I shall agree."

"But still, do you really need to go that far about someone else's weapon..."

"Dao Master Changbin, are you betraying us right now? We are all Daoists, right? We're all friends who cultivate the Dao together, right? Are you abandoning Daoism?"

"...I acknowledge the term, half-sword."

"Then, with three votes of approval, from now on, San'ie is not a dao user, but a half-swordsman."

Hence, there were three swordsmen and one half-swordsmen.

Even if Peng Daesan wished to oppose, he was outnumbered, thus falling into the trap of majority rule.

"Ha. It is too childish to even bother to interact with all of you."

Peng Daesan gritted his teeth and thought.

Was there really any particular reason he had to travel with Qing?

Even he himself couldn't figure out why he had decided to.

However, there was one absolute truth he was sincere about.

{\itshape I shouldn't have done that. 

I should have just let her go on her way. Damn it.}

"Then, should we have the half-swordsman pay for todays snack?"

Peng Daesan growled.

"Are you seriously suggesting I should serve refreshments after hearing that nonsense? You must be the most shameless person in the world. Ha.

"Why? What's wrong? Weren't you at least recognized as half a swordsman? If it were me, I'd be so moved that I'd slaughter a pig and throw a feast for the whole neighborhood. I may even wail in joy. Seriously."

Nan'gong Shencai nodded vigorously in agreement besides her.

Peng Daesans voice dropped an octave.

"I know you do not think before you talk, so you're spouting all kinds of nonsense, but-"

"Ehhhh. You don't have to if you don't want to. Forget it, then. Sword Friend? Aren't you thirsty? Don't you want a cool cup of Longjing tea? 

"If Sword Friend is thirsty, how could I possibly just stand by and watch?"

"Then, can we eat Bingsu?"

Bingsu referred to a snack made from frozen fermented milk.

It was similar to the modern eras yogurt-flavored ice cream.

Except for the slightly moldy smell from the handmade yogurt, the taste and texture perfectly matched its modern counterpart.

Qing was greatly surprised to learn of this snacks existence.

{\itshape To think there are frozen desserts in this uncivilized and primitive ancient China!

Were they not primitives who could only dig up ice and store them in winter?

How did they make this kind of thing?}

It was simply that Qing was unaware.

China of the Middle Ages was a world-leading technological nation.

They easily made all sorts of frozen treats, even in the height of summer.

After all, when it was hot, cold things were the best.

The West, which sprinkled sweet water on snow, were the ones who were actually uncivilized during this era.

Of course, the splendid heritage of medieval China was replaced by the dizzying revelry and pleasure of the Red People. 

"How could just Bingsu be enough? You may also have Mibing\footnote{Red bean shaved ice} and Sulao\footnote{Cold milk}. In fact, you may fill the entire table with cold snacks."

Qing raised her sword and exclaimed.

"YESSIRRRR! That's our Sword Friend! Holy sheee, I'm moved. Let's do a sword ovation! SWORD!"

"BROTHER!"

Nan'gong Shencai shouted 'Brother' and raised his sword.

The swords met in the air and crossed.

Peng Daesan shook his head.

\textit{Putting aside Qing, who was inherently out of her fucking mind, the real problem was Big Brother Nan'gong who indulged her.}

For reference, Nan'gong Shencai was actually considered the best talent among the Hidden Dragons.

Since he was young, he showed extraordinary understanding and an eye for breaking conventions. A genius who understood ten things from just one glance, thus raising the hopes of the entire Wulin.

He was not to be the Sword King but the next Sword Emperor.

If it wasn't for his odd obsession to ascend only through the sword, he might have already reached the Late-Stage Peak Realm. No, maybe even the Transcendent Realm.

百川歸海. Bai Chang Gui Hai. All flows, waves, and streams eventually led back to the ocean.

As such, all martial arts came to a single conclusion at its very pinnacle.

Despite such a concept being a principle of martial arts, Nan'gong Shencai remained fixated solely on swordsmanship.

It was only natural that his realm did not rise.

Nan'gong Shencai, too, was aware of this fact.

Yet, he stubbornly continued, behaving like a Sword Lunatic.

Serious people attracted serious conversations.

But fools were left unbothered.

This was why the Sword King drank heavily every night, straight from the bottle without any cups or snacks. 

Nan'gong Shencai was truly the very definition of a burning filial son. 

Peng Daesan gritted his teeth.

"How absolutely ridiculous."

Right then, Changbin, who had become almost completely silent since Qing joined, sneakily asked a question.

"But Little Brother Peng. This Daoist has been wondering. What exactly is this cool Longjing tea? I have never heard such a terrible thing in my life. Does something like that really exist?"

"Why don't you ask her directly?"

"Ummm..."

Changbin stroked his chin, before coming to a conclusion.

"...That is not so easy to do."

Peng Daesan felt a surge of anger rising from his throat, but swallowed it down, sighing and reminding himself that he should still be respectful to the Big Brother.

In the end, the conclusion of the debate was Qing grinning as she stuffed herself with frozen snacks.

Just like before, it was quite a sight to see her gobbling up food.

For some reason, Peng Daesan found such an appearance annoying.

{\itshape I can't believe it. Regardless of who it is, as long as they buy for her, she just crams everything down her throat. How ridiculous.

Even Heigou raised by the clan would not eat food given by strangers. Yet, she...}

'Okay, and? Did I ask?'

-was what Qing would probably say if she could read his thoughts.

Regardless of what Peng Daesan said, Qing was simply having a good time.

Currently, the group had been traveling west from Huangchuan for three days and were on their second day staying in Xinyang.

This was what traveling with young masters was like.

After reaching a city by carriage, they rested for a day or two depending on how tired they were.

Then, they rented another carriage and departed.

Of course, Peng Daesan, who was relatively frugal, and Changbin, who was genuinely frugal, preferred joining a escort convoy rather than renting carriages and coachmen.

However, among their groups was Nan'gong Shencai, who tore off chits at every bank they stopped at, filling his moneybag to the brim.

Among the Five Noble Clans, the Nan'gong Clan was the second wealthiest. As such, the Young Sword Kings expenditures were the very definition of the God of Wealth, Caishen, descending to the human world.

For reference, the wealthiest household among the Five Noble Clans was said to be in Sichuan or whatever.

It was when they were about to depart since they had rested for two days.

"This is a crossroad. If we go north, it'll be easier and faster. If we go west, we will not see a city for a while and it'll be a longer detour."

"Then can't we just go north?"

"If we go north, it leads to Luoyang."

\textit{Aw, shit. There were ill-fated relationships in Luoyang.}

It was the same situation, whether then or now; her Inner Qi might have increased, but her realm remained the same.

\textit{If only I had reached the Transcendent Realm, I would have gone there and caused a shitfest.}

And there was still the Sudden Mission she had left unfinished.

{\itshape Just you wait and see. Once I reach the Transcendent Realm, I will fucking slaughter you all.

Wash your necks cleanly until then, Black Shadow Association!

No, wait. Was it Black Shallow Association? What was it again? Whatever. Anyway.

Ugh, this damn ancient China. Fucking hell. Whether its sects or people, their names are all so similar. It's confusing the fuck out of me.}

Of course, Qing's face had changed quite a lot.

But with Peng Daesan by her side, they were bound to attract attention and if anything happened, they would have to flee again.

"If we go west..."

"The next city will be near the Dabie Mountains, so it'll take about a week."

Qing grimaced.

A week meant staying in villages or sleeping outdoors.

And in reality, there weren't much difference between those two in Zhongyuan.

From sleeping arrangements to food, it was either a bit more troublesome or the expense of just a few coins to be exempt from such troublesome matters.

But what could be done about it? It seemed like there was no choice.

Qing asked for the groups understanding.

That it seemed they would have to take a bit more of an arduous path because of her.

"I am dismayed. Did I really appear like someone who would ignore Sword Friend's troubles?"

"Uh, as for this Daoist, I-"

"What? You're going to abandon your fellow Daoists? Are you turning your back on the values of status and allocation? Do you not know whose family name I carry?

"-will agree."

Both of them agreed so very cheerfully.

It was truly a relief that she didn't lose her financiers.

As such, they packed their bags and stepped outside.

Strangely, the streets were crowded and the ratio of women was, once again, oddly high. 

But honestly, it wasn't all that strange anymore. Nor did it feel novel.

After ignoring it, they headed to the stable.

That was when Qing witnessed a peculiar situation.

"Please, find my son."

"Agh, hey! You old hag! Who do you think you are to come here?!"

"Aigo, please, my son definitely said he was going to the Daijing Sect. Please. Please, just look for him once. Please"

In front of a small side gate in the imposing wall.

An old woman with white hair pleaded with a martial artist wielding a bang\footnote{staff}.