\chapter{We Are Looking For Someone (3)}

Daijing Sect Leader, Pinnacle of Huangchuan Wang Gouru, was a good person.

Qing didn't even need to check his Karma; she could tell just by looking at the mountainous piles of snacks on the table.

And when she did actually check, surely enough, he was maintaining Righteous Karma, giving him enough of a qualification to be an owner of an Orthodox sect.

While Nan'gong Shencai was strangely keeping some distance, occasionally engaging in conversation here and there, Qing just went ahead and ate.

Bitter-tasting local tea, Banhan tea, was served along with a mountain of Youtiao and two types of Go.  

Youtiao was a snack made from deep-fried dough.

It was one of Qings favorite treats.

After all, it tasted exactly like the twisted doughnuts she used to eat in her hometown. In fact, since the method of making them was actually the same, the taste was obviously identical.

Go referred to a variety of stacks that had been hardened after cooling.

Some were sweet, some were sweet and sour, and others were salty.

Qing never, ever refrained from eating. This was the one thing she absolutely could not hold back on.

After all, she considered the only advantage of this voluptuous body to be its super-capacity stomach.

Come to think of it, all this obsession over food stemmed from her struggling after dropping into this primitive, uncivilized ancient China.

For now, she hastily filled herself up on snacks.

Then, after doing so a while, she abruptly remembered that snacks werent actually the goal at hand.

"Ah. Sect Leader. Do you happen to know a person named Li Xiasan?"

"Li Xiasan? Li Xiasan, you say...Was there such a sect disciple? I cannot recall anyone by that name. Hoho, it is a bit embarrassing for me to say, but I cannot memorize the names of every single sect disciple. But, why is it that you are looking for him?"

"Well, about that..."

Qing recounted the incident that happened at the side gate.

Wang Gouru slapped his palm with his fist.

"Ah, you mean that old woman. It truly is regrettable...But I do not understand why she is asking for him in our Daijing Sect."

"Did you already know about this?"

"Of course. It was a pitiful situation, so I had even inquired about it. But when I did, I found that Li Xiasan was quite a wretched bastard."

"A wretched bastard?"

"He had gotten obsessed with gambling, lost all his family fortune, and even sold his wife to a brothel. It is obvious he must have run away to escape his debts. And then, he proceeded to pin it on our sect. Tsk, tsk."

Wang Gouru clicked his tongue in displeasure.

He didn't seem to be lying.

Qing suddenly remembered the old woman's words.

She said he had taken on some big task from the Daijing Sect, so he could find his wife and live well again.

Finding her? Unless he stored her somewhere, those words didn't make sense.

But if he sold his wife, it meant he intended to buy her back with money. So, such word choice was consistent with that speculation.

That was when Wang Gouru subtly brought up something else.

"Ah. My children are a bit lacking, but they are eager to meet such distinguished guests. May I introduce you?"

Qing looked at Nan'gong Shencai.

A silent conversation of gazes passed between the Sword Friends.

'Is this perhaps the part where we pay for the tea price?'

'That is correct.'

She roughly got it.

Basically, after one eats, they should pay the suitable price of the food. 

Since they had to intrude on his hospitality while waiting for Peng Daesan and Changbin anyway, merely having a conversation with his children should be fine.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Peng Daesan and Changbin returned, their findings were essentially the same.

That he was a bastard obsessed with gambling who even sold his wife.

That he surely must have run away to dodge his gambling debts.

However, that wasn't all.

"There were many who have run away exactly like this. People like Li Xiasan acted as if they had found some big opportunity before disappearing. It was said that all three people, including Li Xiasan, mentioned the Dajing Sect."

"Then, is it related to the Dajing Sect?"

"The amount of ingredients entering the Daijing Sect and the amount of trash left over has not changed during such a time. So, it is probably not a kidnapping case."

Peng Daesan relayed the words he had obtained from an information broker.

It was from a former courtesan who generously shared everything she knew without holding anything back. No, that was an understatement. She practically shared her entire life story.

Just as it had always been since long, long ago, beauty was a form of power as well.

"The Daijing Sects external activities are limited to patrols. There are no personnel sent outside, so apparently it is unrelated to the Daijing Sect."

"Mmm. So, they just ran away? Uhh, what were they called again? The Beggars Union? Did you ask them too?"

"The beggars... Wait, that expression."

Peng Daesan shuddered.

It was that expression again. 

That damn expression that practically screamed she knew absolutely nothing.

"Do you not know...what the Beggars Union is?"

"I guess I don't?"

At this point, he only found it wondrous. In fact, it was almost awe-inspiring.

Hasn't this practically surpassed the realm of mere ignorance?

Honestly, yes. It had obviously gone beyond mere ignorance.

But it wasn't because Qing was ignorant that she didn't know.

It was just that she had no interest whatsoever.

She hadn't sought to learn about it on her own, so she never bothered to ask in the first place, nor had she encountered anyone who would discuss such matters during her travels.

If she had to pick something she was interested in, food would be the only topic.

Ximen Surin was horrified when she saw this side of Qing, thus teaching her many different aspects of common sense.

However, even Ximen Surin could not teach her about such obvious things. After all, she must have known already, right? 

How could one dare to think that there would be the absence of a common sense beyond even their wildest imaginations?

Thus on this day, Qing finally learned about the identity of the Beggars Union, an organization of Wulin.

She also found that the strong beggars wearing those seemingly new ropes were from the Beggars Union.

The beggar with seven knots that pestered her at Anqing was actually a high-ranking person in the Beggars Union, but why would she care about that? Either way, he was lower than Qing in status. 

"They said over thirty people had run away in nearly two months and, despite a majority having been witnessed fleeing, they still found this situation quite strange."

"Then, what is it? They ran away as a group or something?"

"Perhaps someone lured people away promising great benefits in the name of the Daijing Sect. That was what they suspected."

"Oooh. The beggars are pretty smart, ay?"

Qing was impressed.

But then, she suddenly realized something strange.

"But is that all? Why are they the only ones to know? The Daijing Sect doesn't know, though. Shouldn't they have already done some kind of investigation on their own end?"

Peng Daesan replied as if she was saying something utterly ridiculous.

"Are they not just people who lived foolishly and disappeared hoping for some big windfall? Is there really any need to look for them?"

"Eung?"

Qing looked at Nan'gong Shencai.

As such, he spoke as well.

"He is mere trash that sold his wife. It is better for her mother too if he just disappears."

"Ehh? Wot?"

Qing turned her head to look at Changbin this time.    

Changbin, too, nodded at Qing, so very naturally lowering his gaze upon Qings unspoken question.

\textit{What the... Am I the weird one?}

For some reason, Qing felt a bit wronged, thus protesting.

"Are you sure you're right? If someone is plotting some conspiracy..."

"Is it hard for you to handle about thirty Third-Rate martial artists, Qing'er?"

"I mean, of course not?"

The pet name 'Qing'er' came out naturally from Peng Daesan's mouth, but no one managed to notice.

"Even Third-Rate martial artists who know how to wield a word are not a problem. So what kind of conspiracy could thirty people from the gutters possibly create?"

"Oh. Huh."

Come to think of it, that did seem to be the case.

But wasn't that besides the point?

"Big Brother Changbin. Please share your thoughts too."

"Uh. Um. Young Lady. That is. In the first place, it is not particularly our place to interfere..."

At around this point, Changbin sneakily checked Qings reaction.

The hesitant way his words trailed off suggested he wanted to speak informally.

So, Qing nodded in approval.

Seeing as she had already asked to be friends before, it was rather remarkable that he was still being so timid about it.

"It is a matter of the civilians. Ultimately, the government should step in for this."

Inviolability.

Non-interference between the government and Wulin, thus meaning that they should not intrude upon each others affairs.

This was why fights between martial arts were not considered murder and not pursued by law.

Conversely, martial artists who killed civilians and the common people were wanted with bounties placed on their heads. In severe cases, Masters affiliated with the government were dispatched to behead the criminals.

"Of course, there are brave clans like the Yang Clan of Xinchang, who have protected the common people for generations, even at the cost of shedding their own blood. But is there truly a need for the Yang Clan to step in, just because the government is incompetent at fighting off the foreign invaders? Moreover, their estates are inland and have nothing to even do with those pirates."

\textit{The Yang Clan of Xinchang? Hmm, I think that's the same Yang Clan as that guy, right?}

Qing frowned.

After all, she had regarded them as nothing more than child molesters.

\textit{Ah. I wonder. Is Changming doing well? }

She did say she would return when it gets cold, so maybe she could go visit the Divine Maiden Sect after touring the Mount Hua Sect a bit.

Then, she suddenly felt like something was off.

Something, somethingsomething. It felt like she was forgetting something.

{\itshape What is it? Why do I feel so empty?

  It kinda feels like I'm missing something obvious}

Then, the answer suddenly came to her.

It was the Status Window.

To be more specific, a Mission Window had not popped up.

{\itshape Why? 

  Normally, at this point, doesnt something like Sudden Mission! or whatever have to pop up, shitting all over my mood?

  I guess I did feel like I overcame it last time. Did I actually manage to get rid of it through that?}

Qing opened the Mission Window with a sense of unease.

The Mission Window floated up from a corner of her vision and unfolded in the center.

Qings eyes trembled as she scanned through the completed mission.

Sudden Missions didn't appear just anytime.

They only appeared when Qing was insulted or threatened.

Or when she faced a fight between martial artists.

Basically, it meant that it couldn't give two shits about the missing case of an ordinary person.

Qing covered her mouth.

After all, she felt like she was about to vomit out the snacks she had just eaten because of the sudden nausea.

{\itshape Uwegh, this crazy Status Window motherfucker.

  It's a little piece of shit whether it comes up or not.

Were you fucking discriminating even for missions? Based on who the person involved was?

  Then what constitutes Righteous Karma and Evil Karma?

  Are there separate standards for Righteous and Evil Karma? One for the government and another for martial artists?

  What even is the criteria to begin with?

  If the Status Window arbitrarily assigns scores and good and evil don't actually matter

  Then what about me?

  What about everything I have don-}

"Ximen Qing!"

Peng Daesans shout snapped Qing back to reality,

"Are you alright? You suddenly turned pale."

"No. It's not that I'm not alright."

Qings hands trembled.

She was thirsty.

A thirst that neither water nor alcohol could quench.

\textit{Blood. Blood is. Blood is what, blood is what I need...}

But then, suddenly, a face came to mind.

{\itshape Right. I met someone I could kill, huh.

Let's just hold on a little longer. Then, I can finally see some blood tonight.}

"Hooo."

It was right when Qing was trying to calm herself with a deep breath.

"Sword Friend."

Nan'gong Shencais voice, drenched in worry, reached her.

"Why? Sword Friend."

"No, well, its just that...By any chance..."

Nan'gong Shencai hesitated.

It was quite a departure from his usual confident demeanor.

When Qing cocked her head, Nan'gong Shencai continued to speak with great difficulty.

"Come to think of it, the date is roughly...You know."

"What are you talking about? Sword Friend, are you not going to speak properly?"

"No, well, I mean, what I am trying to say is...Wait a moment."

Nan'gong Shencai rummaged through his belongings and pulled out a bundle.

"Right, this. Here, take it."

"What is this? Is it a gift? So suddenly? If you think this will make me happy, then youre absolutely right. But, what is it? A gift of swordly affection?"

Swordly affection. Once again, a weird term popped up.

However, Nan'gong Shencai did not show much reaction, so it was no fun.

"It is poppy."

"Poppy? Isn't that just opium? But why give this to me?"

As Qing unfolded the bundle, the scent of dried leaves filled the air.

It was the trademark smell of the forest, offering tranquility and calm.

"If things get too difficult, just chew on one of these."

"Uh. It's not that bad, though. Anyway. Thanks."

Qing expressed her gratitude, albeit with mixed feelings.

\textit{After all, it feels a bit inappropriate to accept drugs and be happy about it, you know?}