\chapter{We Are Looking For Someone (2)}

"No, old woman, that is enough. Please go back. Your son or whoever did not come here, understand? If you continue to wail like this and they hear you, there will be big trouble for you."

"He definitely said he was coming here.. Please? My son, Xiasan, surely told me he received a big task at the Daijing Sect. He said after finishing the task, he would find his wife again and live well. I am sure of it. Warrior, please, could you check once more for my Xiasan, Li Xiasan."

"For crying out loud. A hag dares...Hurry and get lost. How unlucky do I have to be to get this commotion during my shift."

There was no particular need to intervene.

But there also wasn't any reason not to.

Never in Qing's life had she merely watched a distasteful scene without doing anything about it.

Right as Qing was about to say something

"Look here. Is there a need to be so heartless? You must understand the heart of a mother looking for her child, do you not? After all, you must have a father and mother as well."

Surprisingly, Changbin was the one to step up first.

Qing was shocked.

{\itshape What the heck, he can actually speak!

  And fluently, at that!}

The martial artist corrected his posture upon seeing Changbin.

It was only natural for someone who had trained with blades.

After all, his uniform, adorned with a plum blossom, was the symbol of the Mount Hua Sect.

One did not have the qualifications to be called a martial artist if they did not tense up upon such a sight.

Of course, Qing was in the unqualified category.

"Are you a Dao Master of the Mount Hua Sect?"

"This Daoist is named Changbin. I have intervened because I found the scene I happened upon quite displeasing."

"Ah, Dao Master Changbin. The truth is, this kind of situation has happened more than once or twice now. Initially, everyone took it at face value and looked for a man named Li Xiasan, but he had no connection to our sect.

"Hmmm."

"Even so, she stubbornly continued to come for over a month now, so perhaps I was a bit harsh in my words."

Qing supported the old woman.    

"Granny, are you okay?

"Are you a warrior, Sir? Then please, could you find my son? Please."

"Yeah. Sure. We'll try to find him, so could you go home for today? Your son's name was...?"

"Li Xiasan, it is Li Xiasan. If you say Xiasan of Xiaoming Village, he'll know."

There was a phrase called ZangSanLiShi.

The most common surnames in Zhongyuan were Wang, Li, and Zhang.

And this phrase stated, 'Third son of the Zhang family, fourth son of the Li family', thus referring to exceedingly ordinary people.

If it was Li Xiasan, his name meant he was the third son of the Li family, born in summer.

In Zhongyuan, hundreds of people could come up when looking for a Li Xiasan.

But Qing couldn't just say that she couldn't find her son because his name was too common. As such, she promised to try her best to find him. 

"Ah, thank you. Thank you, Warrior."

The old woman muttered her thanks repeatedly with a relieved attitude and disappeared with a bent back.

Qing watched her go and asked awkwardly.

"By the way, does anyone here know how to look for people? Anyone?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Unexpectedly, Changbin moved deftly.

He asked the gatekeeper for permission to enter and then said to the group.

"This Daoist will ask around the Hao Sect and the Beggars Union. Little Brother Peng will come with me. Little Brother Nan'gong and Young Lady Ximen will stay at the Daijing Sect and gather information here."

From Qing's perspective, Changbin was a far too gentle martial artist with hand tremors, but he was still the Eldest Brother of the Hidden Dragon Assembly.

At twenty-nine, there was no other young Master in Jianghu with a more wide range of experiences than him.

"Oho? Look at our Changbin go. Our friend here was quite a smart one, huh?"

Qing had already declared them as friends.

To emphasize once again, it was not a suggestion, but a declaration.

Since Changbin was on the older side and Qing had a higher status and allocation, why not just say those two qualities were practically the same and be friends, right?

From Qing's viewpoint, it was a significant concession.

After all, strictly speaking, Qing was higher in both age and status.

The only things she was lacking compared to him were wealth and common sense.    

On the other hand, Changbin felt quite burdened.

After all, status usually took precedence over age.

Moreover-

"Changbin'ie is soooo reliable. Iyaaa, how reassuring."

Qing kept poking Changbins side with her elbow.

{\itshape ...What kind of woman behaves so freely with a man?!

  In a world where men and women were distinct, how could she be so informal?!

  How could a woman not know to be modest?!

 '..Could she perhaps have feelings for me?}

Of course, Changbin, rather, was the one who actually became modest in front of women.

He averted his gaze with a flushed face.

"That...Let us go, Little Brother Peng."

Peng Daesan looked at him as if finding him pathetic and then spoke.

"By the way, Big Brother...Do I have to go with you?"

"Of course. Did I not say we are going to the Hao Sect, after all?"

The Hao Sect was the most peculiar union in Jianghu.

Originally, Hao referred to the five most humble professions in Jianghu.

A sect meant for such lowly people.

Essentially, it was a gathering of those living at the very bottom of society.

One might wonder what such people, the lowest of the low, could accomplish, even if they gathered together.

However, they leveraged their specialties to exert their own kind of strength.

Namely, their incredible stealth techniques that made them practically invisible to others!

These lower-class lives were masters of stealth, thus indiscernible.

When people in Zhongyuan sat in an inn, they did not notice the servers cleaning the floors.

Even if they were seen, they did not think such lowly beings could even understand human speech.

Porters, coachmen, and boatmen were also treated as invisible.

Peddlers and courtesans were regarded as if they were deaf.

Through this, the Hao Sect became the foremost information dealer of information, as well as a jack-of-all-trades enterprise dealing in smuggling, black market trades, brokerage, and more.

And the sellers of information in the Hao Sect were beautiful courtesans.

Those who actively utilized the weapon of womanhood.

They were adept at overcharging while selling information and skillfully extracting information in return.

Yet, there was someone who could exploit the weakness of any and every woman.

The one who exuded such majesty was the Most Handsome Man Under the Heavens. 

"Little Brother Peng coming along will surely yield proper information. After all, those individuals have reached a state of mastery when it comes to ripping people off."

Peng Daesan was immediately convinced.    

Meanwhile, a face poked out of a sects side gate.

It was the Daijing Sect's Leader, Wang Gouru \footnote{Wang Gaeyuk in the original text. Gouru/ Gaeyuk means 'dog meat'. Not making this up}

Originally, the side gate was a passage only used by servants, kitchen staff, and the like.

It was not exactly dignified, nor honorable, for a Sect Leader to be seen using it.

However, this was the conclusion Wang Gouru had come to after much contemplation.

After all, it was also true that guests usually did not come to the side gate. Especially such distinguished ones.

"This place does not seem to be suitable in welcoming such esteemed guests, so please let me escort you through the main gate."

It was a compromise that satisfied both parties.

Since the Sect Leader personally welcomed them, there was no shame in facing the guests, and since he did not cross through the side gate, his dignity remained intact.

From the guest's perspective, they did not pass through the side gate and the homeowner personally came out to greet them, a move that could be considered admirable.

But to Qing, all she could think was 'Why? Whats the point?'.

"Ehhhh? Do we really need to go through the main gate?"

"I understand Sword Friend's free and easy manner, but a true man does not enter through the side gate. As Sword Brother is also a peerless swordsman, you must always keep this in mind."

In other words, entering through the side door was considered a disgrace for a swordsman.

Qing just accepted it as was.

{\itshape Just as expected of the original long legs.

  Look at them making a big deal out of useless shit.}

While the guests were led along the tall walls of the manor, Daijing Sect Leader, Wang Gouru, felt somewhat disappointed.

He had heard that a Daoist from the Mount Hua Sect had arrived.

Wang Gouru had also heard of the rumors that the Jade Qilin had entered the city.

As such, it was easy to guess who exactly the Daoist of the Mount Hua Sect and his party were.

But what was this? It was just a young swordsman and a pretty girl in martial attire.

The young man was indeed personable, but he did not radiate the brilliance of the Most Handsome Man Under the Heavens.

It really seemed like they werent at a level where the Sect Leader had to personally show his face.

'Had he acted too hastily?' That was what he was thinking.

Thus, his eldest son, Wang Xunxi \footnote{飧汐 'evening tide'. Wang Sonseok in the original text}, who was in training, came out to greet the guests instead.

Wang Xunxi belonged to the Earthly Courage Team and immediately recognized the unexpected visitor's face.

"Great Expert Nan'gong Shencai! It is an honor to have you visit our sect! My name is Wang Xunxi. Do you perhaps recognize me? We have met a few times at the Alliance."

"Is that so? Pleased to meet you."

Wang Xunxi was slightly taken aback.

After all, Nan'gong Shencais attitude was quite lukewarm.

"Great Expert?"

"To think the Daijing Sect was a half-sword sect. But since we are comrades of the same Orthodox Faction, I have no choice but to try to understand. Apologies for the sudden visit."

{\itshape What in the world is a half-sword sect?

 Perhaps the reason for the successor of Nan'gong's chilly demeanor lies in that term called a half-sword sect.

  Did our Daijing Sect do something wrong?}

However, Wang Xunxi could not even begin to guess what exactly it was, so he had no choice but to break out in a cold sweat.

For reference, as a member of the Orthodox Faction, he was someone who had always prided himself on maintaining the dignity befitting such a status.

"Ah! I apologize. This is not the time for me to be asking such things. Is there anything you need? What can I do for you? Will you be staying the night?"

The meaning behind such questions was whether they were going to stay for dinner.

That he needed advance notice in order to prepare.

"I am not sure, but there are more in our group. After all, the Drunken Sword and Jade Qilin have gone to take care of some business. However, they should be back soon."

This implied they were not sure about staying for the night, but did intend to have dinner here.

That there were more people coming, so they should prepare as such.

"Oh, oh!"

Wang Xunxi's face lit up.

There were a whopping three members of the Heavenly Martial Team.

And even among such a group, they were all true Hidden Dragons, at the level of successors to their respective affiliations.

Such an opportunity to build personal connections had come knocking, so naturally, he could not help but be delighted.

"Then, this Young Lady here is..."

"I'm Ximen Qing."

Her introduction was a bit brief.

It implied she was an unknown without a clan, sect, or title to her name.

She was a fairly pretty young girl, as well as a swordsman, so he assumed she was just someone they were bringing around. After all, at least one of such women was usually present as company..

"I see. So you are Young Lady Ximen."

Wang Xunxi instantly lost interest.

There was no benefit in getting too familiar with the woman of a Heavenly Martial Team member. After all, it wouldn't end well for him.

"But Great Expert, will the rest of your party be much delayed? Father has prepared some refreshments."

"Oooh. Refreshments. You're quite courteous, huh? Hey, Sword Friend. Is it right for me to join as well in these situations? Ignoring delights that had already been prepared would be rude, right? Can you say I'm right?"

"Of course, that is only natural. No sect, union, or clan would dare to neglect someone like Sword Friend."

So, when such a conversation came up, Wang Xunxi was quite taken aback.

He roughly understood what Sword Friend meant in this context.

But to think she was a woman with such significance that even the successor of the Nan'gong Clan himself would use the word 'dare' to describe how she should be treated.

{\itshape What is going on? Is she the future lady of the house?

 I should have been more welcoming earlier. Shoot!}

Wang Xunxi elevated his evaluation of Qing by at least three stages.