\chapter{We Are Looking For Someone (5)}

From the aspect of extracting information, torture was remarkably inefficient.

Torture was an act that brought forth the antipathy of the opponent.

As such, how could one trust the information divulged by a target whose hostility had been heightened to the extreme?

Moreover, the person being tortured would gauge the torturer's reactions in order to somehow escape the moment.

It became a situation where they said what the torturer wanted to hear, instead of actually conveying accurate facts.

However, for Qing, this was a fact she didn't know anyway.

And even if she had known, she wouldn't have cared.

There was a deep-seated malice embedded in her heart.

A powerful urge that always whispered persistently.

Blood and blood. And even more blood.

Screams. Outcries of pain. Blood phlegm boiling, surging up in wheezes. Weak breaths, barely clinging onto life. Tears swallowed down to stifle the wails.

Pupils that all had different charms, whether they were unfocused and dully open, trembling fiercely without being able to settle, or expanding into emptiness/distrust when intuitively facing death.

All those moments of pain were so very beautiful.

As such, her body trembled violently and she could not hold back her ragged breathing; every nerve in her body, every bone and joint, every muscle felt like it was ablaze with a horrific pleasure. 

{\itshape Ah. So this is why artists go crazy.

  Why they continue to paint, even while ingesting mercury vapor, and continue to write, even while coughing up blood due to tuberculosis.

  Then, even if their lives end short, it must not have been a misfortune.

  After all, they must have lived happily until the very end.}

Therefore, Qing's approach was different from torture.

It was closer to a quest for truth or a religious ritual of worship.

She gauged the damage inflicted on the subject through groans, screams, and breaths while dissecting the flesh and turning muscles inside out.

It was a study, an effort, to understand how to keep a life… alive while dissecting it alive.

All for the sake of inflicting more pain.

Hence, Qing's touch was delicate and cautious.

After all, it was her one and only educational material in this study. A test subject she could only experiment on once in a blue moon.

Suddenly, Qing's hand stopped.

\textit{Ah. Fiddling with more might be a bit dangerous, huh?}

It was a baseless intuition.

\textit{Ahhh, come on. And it was going so well.}

Qing stepped back, licking her lips.

"Please, please, I would rather you just kill me, please…….."

Wang Xunwan, who had turned into a lump of blood in the shape of a human, begged. 

His vocal cords, overworked by the screams, produced a sound akin to scraping sand and his squeezed lungs failed to even function properly. 

"You… You've done something bad, right?"

Qing giggled.

"We're secret friends, right? Can't you just tell me a little? Only me? What did you do to score over three hundred points?"

{\itshape Yeah. I really should've discovered this first.

  What in the world was I doing, merely slashing throats without a care?

  Have I…lived too thoughtlessly? 

  I admit it. Seems like I need to reflect a bit more.

  But, it's the world that's wrong anyway, right?

  Look no further than this scum. He was kidnapping innocent people, who were just minding their own lives.}

"I, I deceived people……."

"Ah. The missing people?"

Qing cocked her head.

"Nahh, no, no. Come on. That's not it. Do you really think merely doing that would score you minus three hundred points? Is deceiving people really that bad of a deed?"

"I knew…those people…wouldn't…return……."

"Ah. So even though you knew, you sent them to their death? That kinda makes sense. So, how many did you send?"

"Two, three a week. It has been over half a year."

"Eh? What the… Okay then, let's just say it's 2.5. Then that's ten people in 4 weeks. If it's over half a year, that's roughly over sixty people, huh? Mm. Mm. Yep yep, makes sense. That checks out."

Qing nodded.

{\itshape Sending at least sixty people to their death must score about three hundred points of Evil Karma, huh.

  No, no, wait. That doesn't sound correct, right? Wait.

  Doesn't killing bad guys give Righteous Karma?}

"Is that all?

"Demonic Arts… I also practiced Demonic Arts."

"Demonic Arts? What kind?"

"Heart Absorption Arts……."

Once again, it was a situation of ‘Qing doesn't know martial arts anyway'.

But just from hearing the name, she felt like she somewhat understood what it was.

\textit{  Heart Absorption Arts. Isn't it like a martial art that eats hearts?}

In fact, it was an even more malevolent Demonic Arts than Qing thought.

Heart Absorption Arts was a degenerated secret technique of esoteric Buddhism, increasing Inner Qi by consuming hearts refined through alchemy.

To complete the Black Heart of Heart Absorption Arts, one had to transfer the Innate True Qi of a nine-years-old child into their heart, a process accompanied by terrible pain.

Moreover, regardless of the practitioner's talent or constitution, their achievements increased merely by the number of hearts consumed.

In reality, even after achieving the Grand Star, it wasn't like there was some significant enhancement of Inner Qi.

However, the issue was the horrific method of practice and the possibility of quickly producing Masters of only Inner Qi.

That was why Heart Absorption Arts was widely known as a dreadful Demonic Art.

"So, you've eaten hearts, huh?"

"Because those people brought them………."

"Those people?"

"I don't…know their identity, really, truly, I don't know."

He didn't seem to be lying.

Qing gently rubbed the back of her neck.

"But why, though? Why do you need to learn Demonic Arts so badly that you would sacrifice people to bastards you don't even know? On top of that, you even ate human hearts, you know? Wait, no, that might actually taste good. Are they fresh when they arrive?"

"What……"

Qing slapped her own cheeks a few times.    

"No, fuck. Cannibalism is not the move. Sorry. My mind is a bit scattered. Anyway, why? Why go that far?"

"I-I wanted…to become…the S-Sect Leader……."

Huh, he's a bigger piece of shit than I thought.    

He said that the organization of those people were working on something with the common people they had abducted, and when it was finished, they planned to attack the Daijing Sect.

At that time, the eldest son, Wang Sonseok, was to be gravely injured and the second son, Wang Xunwan, was expected to make a heroic appearance and repel the enemies.

Only then did true joy bloom in Qing's heart.

{\itshape Ah. So, Evil Karma is finally proving itself, huh? It really does track evil accurately.

  Looks like they were all fucking pieces of shits anyway. Good fucking riddance.}

She confirmed that the hobby she had pursued until now had indeed contributed to world peace.

Basically, she now held a newfound sense of accomplishment and pride.

"Now that…I've told you everything… Will you spare my l-"

"The fuck? Weren't you asking to be killed earlier?"

"Please……"

An opponent that couldn't be communicated with was terrifying.

Qing had previously been in that very state, studying the mysteries of the human body with astonishing focus.

But it seemed that after they talked, a faint hope that he could live must have sprouted. 

"Well. I'll be generous. Thanks to you, I've also solved a dilemma, so."

"Then, will you spare………"

Despite his face being completely skinned of its leather, a vivid hope blossomed on that face.

The will to live was indeed remarkable.

Of course, the people this fucker sold away must have felt the same.

But he couldn't be killed yet.

After all, she had taken such great care not to let him die until now; killing him now would make everything go down the drain.

"Well. Fine. I'll overlook it this time. So, always be grateful. Understood?"

And so, fun time is over!

\textit{Fun times always seem to pass so quickly.}

Qing, finding it a bit of a pity, roughly threw Wang Xunwan onto a blanket and dragged him outside.

Although this situation was not what Wang Xunwan had previously imagined, he did technically end up lying on a blanket.

So, he achieved his goal, at least in part.

Qing opened the iron door and stepped outside.

By then, the sun was already shining brightly.

Come to think of it, the bastard was a shitty little fucker from the very start. After all, when asked whether he knew any places where sounds wouldn't leak, he instantly guided her to this suspicious basement.

It was probably a place where he secretly ate hearts and met those unknown people.

Surprisingly, Qing was in a rather clean state.

Of course, her sleeves were sticky, her face was smeared with the blood from her hand, and her nape was crusted with flakes of dried gore.

But compared to her usual utterly disheveled appearance in these situations, she was extremely clean.

Since the basement wasn't far from the Daijing Sect, Qing soon encountered the Daijing Sect's dao wielders.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The day had just begun, but the Daijing Sect was already very busy.

After all, a precious guest had gone missing and the second son also didn't show himself, compounding the issue.

Taking note of their guests' discomfort, they sent out sect disciples in search of them.

However, Daijing Sect Leader, Wang Gouru, wasn't particularly worried.

He thought they had probably just gone out for some morning errands.

The young Masters of the Hidden Dragon Assembly seemed worried, but Huangchuan was not inherently a dangerous city.

Wang Gouru firmly believed that.

So, when the guest dragged something in and claimed that something was Wang Xunwan, he almost collapsed in shock.

After all, people were weak to unexpected surprises.

But little did he know; that was just the beginning.

It was because of what the guest said after he urgently sent his second son to the medical hall.

"He deceived the missing people and abducted them. I heard it myself. He planned to collude with bad guys to kill his older brother and take over his position as successor."

"It cannot be! Is there any evidence, any proof? That punk might be rude, but he is not the type to concoct such evil d……"

"He practiced Heart Absorption Arts, though? If we call a Master, wouldn't they be able to tell?"

"Heart Absorption Arts!"

Wang Gouru staggered, letting out a lamentation.

Wang Sonseok quickly supported him from behind.

"That, that……."

If Wang Xunwan really did practice Demonic Arts, it wouldn't be hard to verify.

And why would anyone lie about something that could be so easily disproved?

It was the perfect evidence to back up the situation.

Then, Qing clapped her hands to draw everyone's attention.

"Now, then. Onto the next topic. I also found out the place where that unknown organization took people, you see?"

Qing stared directly at Wang Gouru and continued.

"You know the Daijing Sect is ultimately responsible, right? So, shouldn't you come along then?"

The ones dragged away were nobodies, those who no one would care about even if they disappeared into the abyss of their wretched lives.

As such, she wasn't really saying, ‘Let's go save them!'.

If they happened to be alive, then sure, they could be saved.

But honestly, she didn't really want to put effort into saving a piece of shit bastard who sold his wife to cover his gambling debts.

But what about those left behind?

Qing remembered the face of the granny who had begged her to find her son, her expression filled with desperation.

Even if she didn't have much time left, the granny still needed to live out her remaining life.

She shouldn't have to spend her days clinging to these half-swordsmen, begging them to find her all-grown son.

Who knows? Perhaps Lee Hasam could truly wash his hands clean of the past, find his wife, and live properly for once.

Or maybe he'd end up like those gamblers in that Gangwon Hell1there is only one casino in korea where KOREANS can play in. and that is in Gangwon province of her original world, where those hungry ghosts sold off their family like the motherfucking bastards that they were.

But still, at the very least, those left behind shouldn't have to remain trapped in false hope and lingering regrets just because of a bastard like that.