\chapter{Rice Blocks (12)}

Everyone has moments in their lives when they want to scream.

Imagine this.

What if you hear a loud noise that makes your head feel hot, spicy, and painful, as if it were on fire?

And what if, on top of that, something gets in your eyes and makes them sting and water?

That would be a hundred times worse than holding back a scream.

You would want to scream out loud.

But that's not all.

What if you had to run around in a humid, sticky day while in that state?

What if instead of refreshing sweat, you were covered in unpleasant, sticky sweat?

You're covered in a layer of sticky sweat, and every time your skin brushes against something, it feels unpleasantly slippery due to its subtle viscosity.

But that's not all.

Add dirt to the mix.

Your face was covered in dirt, and every time you wipe away the runny snot, it feels like a scrub brush was scraping across your skin. Your hair feels like someone poured a handful of sand into it, and every time you scratch it, the dirt digs into your fingernails.

There isn't a single spot on your body inside your clothes that isn't covered in dirt, and every movement causes the dirt to roll around and sting.

But that's not all.

What if you add filth to the mix?

Both the Five Poisons Sect and the monsters spit venom, and the monsters even spread pieces of rotten flesh and blackened internal organs from their dead bodies.

The stench of decay was an added bonus.

Even the enemies continue to administer the poison.

The Oedokmun followers, even as they die, struggle to deliver one last poisonous sting, clinging to their enemies' arms and legs in a slimy embrace.

And the Blood Cult's poisonous monsters were just monsters, with no joy or satisfaction in cutting their enemies.

Meanwhile, the skilled ones among them escape with strange movements, throwing spears, daggers, and poison pouches.

When you chase after them, they run away again…

It's a million times more unpleasant than anything else.

I've never felt such immense discomfort, filth, roughness, stickiness, The despicable tactics of these creatures were getting worse, and my nostrils were burning with a fiery heat, my eyes were stinging, tears were streaming down my face, and snot was running down my nose. If I try to wipe it away, the dry dirt scratches my skin…

"Kraaaahhh!!"

This was not a matter of Qing's patience.

This was truly an extreme situation.

Honestly, even if you brought Buddha himself here, it would be impossible to remain rational in this situation.

This was acknowledged by the three great masters of the Three Realms: Jungwon's representative Yikgeunseokgi, Seojang's representative Mansangyeokgi, and Seoyang's representative Yongsaengbanyagi.

There's no choice but to explode, he thought.

So, inside Qing's dantian.

The little girl in blue, Wolnyujinki, looked at the little girl with four hundred eyes standing in front of her.

Kwang-sal-ma-gi, the only purple-robed monk among the Qing monks, gazes at Wol-nyeo-jin-gi with eyes shaped like axe blades, his expression somehow sad or aggrieved, yet compelling.

A moment later, Wol-nyeo-jin-gi turns around.

The three monks nod their heads.

Joo Yang-jin looks displeased but nods in agreement.

Below them, Hwan-hee Jin, wearing a noose around his neck, bares his teeth and causes a commotion.

No one has said anything, but it was an unspoken rule that Jin of golden color or lower have no right to speak.

Finally, Wolnyujin-gi looks at Gwang-sal-ma-gi with his usual indifference and expressionless face.

Then, Gwang-sal-ma-gi's pea-sized eyes shrink to the size of grains of rice.

Then, he proudly draws a small knife and raises it high.

Following this, with an expression of excitement, he raised the sword high and charged forward. Behind him, the purple lightning-streaked Zhen Zhen Maqi, the red-clad pair of Xue Yun Maqi and Ma Wang Xue Qi, and the other Maqi flew and leaped vigorously, spinning in the air and bursting through the Dan Tian gate, all charging forward at once.

Why do the immortals of Buddhism and Taoism, who were supposed to maintain a clear and pure mind, tolerate the chaos caused by the demons?

Sometimes, maintaining a clear mind can be harmful.

In terrible situations, letting go of your mental grip can actually be beneficial to your mental health.

At a time when all kinds of irritation were rising from the tips of your toes to the back of your throat, there was no point in enduring such irritation and letting it burn inside you.

It was not about craving slaughter, nor was it about killing the living to take their pain, which was an explosion of cruelty.

Besides, it might be good to vent the pent-up anger in your heart once in a while.

As someone in Qing's hometown once said.

When it comes to satisfying your desires, it's best to do it properly. If you do it half-heartedly, the poison will remain in your heart.

And so, after a long time, Maggi was back in full force, or as the martial artists would say, the great rampage of evil has begun.

…In the midst of this, a different kind of magic, stuck in the corner, quietly raises its head from between its knees and looks around cautiously.

Then, somehow, it wriggles toward the dantian gate while remaining seated.

At that moment, Joo Yang-jin drops the noose he was holding in his hand.

And with his spirit broken, Hwan Hee-jin, dressed in a shameful outfit that could be described as either clothed or naked, shoots out like a firework with his tail on fire.

And then, thud, thud, thud, thud.

Kuk… Kkuk…

The Demon King was laughing again today…

Urr, a low, threatening vibration like that of a beast flows from Qing's mouth.

His eyes have long since rolled back in his head.

"Go on, it's your turn, monster!"

O Dok-mun opens the bars holding Dok-chu, the monster provided by the Blood Sect, and shouts.

However, Dokchu, who usually bangs on the bars and breaks them with his head in his eagerness to escape, was curled up on the other side of the iron bars, unwilling to come out.

"Kiee…"

"No, why were you doing this? Go, go! The enemy, Heavenly Blossom Sword, was over there!"

O Dok-mun reaches through the iron bars, grabs Dokchu's head, and pulls him back.

However—

"Kieeeeeeeeeeee

Although Dokchu was almost completely devoid of intelligence, if he could speak, he would have said this.

No, Master. Even if I am a monster, isn't it too much to force me to fight that thing? It's inhumane, no, it's Dokchu-like. It's unreasonable.

O Dokmun looks at the direction in which Dokchu has run away with a bewildered expression.

At that moment, a breath tickled his ears.

Shiiiiiiiiiiiii

"Ugh!"

O Dok-mun fell backward in shock.

Then, the upper half of Cheonhwa Sword's body vibrated up and down. It looked as if he was laughing maliciously.

O Dok-mun's expression changed drastically.

As if angered by the momentary look of surprise and fear, Odok Mun-do's face quickly turned hateful.

However, contrary to his fierce momentum, which seemed as if he was about to rush forward, he crawled backward with his buttocks and arms.

The Cheonhwa Sword shook its upper body again, as if to say, "Try to run away if you can."

Five Poisons Sect-do clenched his teeth and turned his back.

As Five Poisons Sect-do pushed through the trees, he heard light footsteps, tap, tap, tap, coming from the same distance behind him.

It was as if he was being told to run away if he dared.

Five Poisons Sect-do's teeth gritted.

He wants to release all the poison in his body right away, but he has already received his orders.

So, Five Poisons Sect-do follows the path he has trained himself to follow and heads for a specific point in the formation.

How long does this go on?

Suddenly, in the middle of the tropical rainforest, a large clearing appears, created by cutting down trees and leveling the ground.

And in that space, yellow tents were densely packed.

Outside, a warrior wielding a crescent sword rushes out and thrusts the tip of his sword at the Five Poisons Sect-do who has just emerged.

"Stop! Who were you?"

It was a slightly awkward Zhongyuan accent.

But before the Five Poisons Sect-do can answer,

"Heeek, Makaron! Makaron!"

The warrior points behind him and yells loudly!

With a voice filled with uncontrollable fear, Qing's lips open wide, almost touching his ears.

Finally, at last, he has found someone who was reacting properly.

"No, that's not it! They're the enemy!"

Five Poisons Sect-do yells loudly.

Then he rushes across the open space between the tents, shouting wildly.

"Enemy attack! The enemy was here!"

Finally, a middle-aged man in splendid golden armor blocks Five Poisons Sectdo's path.

"Hey, man from Zhongyuan, this was our territory. No matter how much you were affiliated with the Blood Sect…"

At that moment.

Kraaah!! A piercing scream cuts off the middle-aged man's words.

Turning his head in panic, the middle-aged man utters a word with a strange pronunciation.

"Makaron…?"

Splash, blood spurts into the sky.

I don't know how he was struck, but I see a head flying through the air in a parabolic arc.

The middle-aged man's expression contorts.

"You, Zhongyuan…! \#\#\#! \#\#\#\#\#\#! \#\#! \#\#\#\#\#!"

In an instant, words that were not Zhongyuan's language burst out, and warriors wielding weapons rush out from the tents.

And then, ding ding ding ding

The sound of bells ringing loudly fills the air.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

If you drink salt water because you were thirsty, no matter how much you drink, your thirst will not be quenched.

But what if you drink water?

How refreshing, exhilarating, and delightful it would be to pour water down your parched throat!

This was the reason why Qing's eyes lit up again.

Something new has appeared, and they look clearly afraid. This was going to be a slaughter, isn't it?

But who were these guys?

"Wait, vampires, calm down! We're on your side! We're here to help your Blood Cult!"

"Who's the Blood Cult?"

Qing yells and swings his arm.

A huge hand overlapped his hand, and long nails twisted like dead wood chopped the warrior into pieces.

Qing did not need to study foreign languages.

This was because automatic translation was supported for any language he heard.

However, he could only understand what was being said, not which language it was.

They were just barbarians, but why were there barbarians here?

It was the same in the preface. It seemed that the Blood Sect couldn't wield any power in Zhongyuan, so they were borrowing the power of barbarians.

In any case, if they were here to help the Blood Sect, there was no reason to show mercy.

Qing shouted.

"I am Yummi Dokryeon!"

And once more.

"I am a rice-eating Dookryeon! I will take your lives! Surrender your necks!"

Fluent barbarian words burst out.

I don't know what language it is.

"Heeek! You rice-eating bloodsuckers! We'll eat your rice and suck your blood! We'll kill you all!"

One barbarian screams and runs away.

But that lasts only a moment.

Splash! Blood gushes from his throat and splatters on the ground.

A middle-aged man in splendid golden armor swings the large crescent sword in his hand and wipes the blood off it.

What? Why were you killing your own allies?

"Listen, warriors of Daewol! Warriors of Daewol do not flee from their enemies. It doesn't matter if they were humans or ghosts! Warriors of Daewol were warriors who slay ghosts, aren't they?"

Ah, Daewol. They were barbarians from the Kingdom of Daewol.

Now that I think about it, the southern ridge of Dochae Mountain was the border with Daewol, so it makes sense that the barbarians here were from Daewol.

Of course, whether they're barbarians from Daewol or Burma, what does it matter?

There was no reason to spare those who came to help the Blood Cult just because they were barbarians.
