\chapter{Rice Blocks (5)}

If you know your enemy and know yourself, you will not be endangered in a hundred battles. This was a very famous saying.

Of course, it was a simple truth, but how easy was it to know your enemy?

Conversely, it means that no matter how hard you fight, if your enemy knows you, they will never be cornered.

Therefore, one of the old pieces of advice passed down in the martial arts world was to hide 30\% of your abilities so that your enemies don't know your true strength.

A proper organization would desperately seek ways to protect its information.

And the easiest and most convenient way to protect an organization's information was to not give it to its members in the first place.

That was the method used by the Blood Cult.

So, Qing thought of her honest conversation with Dong-juk and licked her lips.

\textit{Hmm, that guy didn't know much.}

\textit{Still, it wasn't a complete waste of time.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Previously-

After listening to Dong-juk's voluntary testimony, Qing's impression was simple.

"Start over from the beginning."

"What?"

"Start over from the beginning. Don't miss a single word."

Gathering information was difficult.

Even after gathering information, it was difficult to trust it, so believing the words of one person without cross-checking was foolish.

However, the human brain has its limits, so when asked to repeat everything from the beginning, it was not easy to remember the parts that I made up.

"You bastard, you're saying something different from before!"

"What did I say before?"

"Are you trying to trick me? You're still safe, so you're getting greedy? I'm confiscating one of your eyes. You have two, so one is fine, right?"

"Wait, wait! Aaaah!"

"Okay, I'll forget what you said before. From now on, be honest."

Isn't this the fun part of gathering information?

And so, again. And again.

The Blood Cult was centered around the Great Ones who could hear the voice of Blood Maitreya\footnote{A Buddha that's prophesied will descend in the future} directly.

POW! Qing hits Dong-joo's head.

"What Blood Maitreya, you idiot? It's Blood Ma\footnote{Demon}."

"Yes, yes, Blood Demon, under Blood Demon…"

Blood Demon, the leader of the Blood Cult, commands terrifying masters as his subordinates, who were called Great Masters in the Blood Cult and have formed branch groups based on their specialties.

Dong-juk belongs to the branch of the Sword Demon, the Blood Sword Corps, and his mission was to protect his compatriots in Yunnan with the Blood Warriors.

"Blood Warriors?"

"That's what we call warriors who haven't been accepted into a branch yet."

It sounded like they were basically new recruits.

Blood Warriors were recruited by each branch based on their achievements and talents.

Those who have no talent or ability were not taken in, and were sent here and there to do security and other odd jobs.

Is Sword Deon here? That can't be.

Then who was here? I heard that the Blood Warriors under Blood Poison Corps were here.

Then is Poison Demon there? I don't know.

What kind of plot are they hatching in Yunnan? I don't know.

What do you even know? Who is Zheng Liuzhang? He is the son of Zheng Mang of Blood Swords Corp, the right-hand man of the Sword Demon.

\textit{Oh, come on.}

\textit{He's not even the Sword Demon's son, just the son of his right-hand man and confidant. He's just a small fry.}

And in fact, right-hand men always think more highly of themselves than their masters do, so there's no guarantee that the only person who considers himself the right-hand man of the Sword Master was that guy Zheng Mang.

In any case, Zheng Liuzhang had no talent whatsoever and was so clumsy that he's worse than a third-rate fighter, but thanks to his father and brothers, he's been given missions that were easy enough for him to succeed at.

"He have older brothers? Oh, that's what was bothering me. Are their names something like Jung-ho and Jung-jang?"

"They were Jung-soo and Jung-jang. Captain, ah, yes, Jung-mang was told by a fortune teller that his children's names should contain the word 'water.'"

Su, Ji, Ryu, all have the character for water in them, but it felt like a slap in the face.

"Um, can I go now…?"

"Huh? Where are you going? That's not what we agreed."

"What?"

"I said I'd spare your life, not that I'd send you away unharmed. And the first thing I hate most in this world is a traitor. You betrayed your own people just to save yourself? You're finished."

"No, the promise was different, ahhh!!!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{Hmm. That was quite entertaining. Perhaps we should do it again next time.}

\textit{While I was starving, I thought it would be nice to taste something delicious just once.}

\textit{But now that I've tasted it, I can't stop thinking about it.}

Humans were so fickle.

Still, Qing can't help humming a tune.

Now, the songs of her homeland, whose titles she couldn't even remember, and Zhongyuan, which was not that primitive, were not very diverse musically.

Qing's voice cut through the silence.

In every city, there were always ironworks near the outskirts, near streams.

Before she knew it, the sound of hammering fills the air.

Qing pricked up her ears and listened to the sound, then followed the clearest, deepest sound of iron being struck.

As she entered the ironworks, the heat hit her like a blast.

As the hammer struck the iron, the blacksmith casted a wary glance at the female swordsman holding a large sword.

Qing held out her palm, signaling them to continue what they were doing.

A moment later.

With the sound of boiling water, the blacksmith wiped the sweat from his brow and spoke to Qing.

"I'm sorry, but we don't handle swords here. If you're looking for a sword, go to the third shop on the left, the ironworks owned by Mr. Ban."

"Oh, I'm not here for swords. Do you happen to have any good iron plates? The sound here was really nice."

No blacksmith would be upset to hear that the sound of hammering was pleasant.

With a softer expression, the blacksmith asked again.

"You mean an iron plate? I need to know what kind of iron plate you want, whether it's steel or cast iron, and how big and thick it is. Yes, what are you going to use the iron plate for?"

"Ah. I want to put it on my chest."

"Huh? What, put it there?"

"Yes. Like this?"

Qing hesitantly placed her hands in front of her chest and made a gesture as if feeling a watermelon.

The blacksmith expression turned bewildered.

"You want to put the iron plate there?"

"Yes. It's just so uncomfortable. Since I have no muscles, it's like a piece of paper with holes in it. It's heavy, it sweaty, and when I wear clothes, it bulges out and makes me look bigger. and everyone keeps glancing at it. There's no single good thing about it."

"No, that's… Ahem, you must be going through a lot…"

"Anyway, I'm going to put something inside my clothes."

Qing did learned from experience.

She has already suffered serious damage to her chest padding several times.

In fact, it can hardly be called padding.

Because it stick out on its own, it got caught on blades that shouldn't hit it, and if it shook, it hurts, and there was a strange resistance to movement due to unnecessary recoil.

Of course, her physical durability was beyond that of a human, and she had already lived for more than half a century, so she was already used to life difficulties.

Furthermore, even if she were to wore iron plates, the chest was a vital part of the human body, so in order for Qing to get stabbed in the chest, they would have to be at least a master of Harmony Realm or one of the lucky ones among those who gathered like a pack of dogs.

What use was iron plate against Sword Force? That was why martial artists did not wear armor.

In front of Sword Force, iron was like paper, and if you were hit properly, you will die, so rather than wearing heavy armor, it was better to wear a martial arts uniform and hold out with defensive techniques.

In addition, martial artists do not wear armor because they were light on their feet.

Overwhelming attack power must be defeated by striking or evading, not by defense.

However, this time was a little different.

From watching Tang Lan-Ah, she realized that the fighting technique of poisoners was to throw something coated with poison.

And since most hidden weapons were small and light, it was difficult to pierce iron plates even with considerable force.

Of course, even if they pierced Qing's enormous chest fat, they would not be able to pierce the superhuman pectoral muscles behind it, or even the muscle layer that acts as an automatic self-defense mechanism.

Still, it would be extremely, extremely painful.

If it was only a prick, it might be okay, but if the hidden weapon pierces all the way through, it would be extremely difficult to remove…

Thus, Qing came up with a genius idea.

A steel chest armor!

The underwear culture in Zhongyuan was limited to covering the upper body so that nothing would show or stick out, so this was a truly timeless idea.

However, the blacksmith was at a loss.

"How should I make it? Should I make two iron buckets?"

"Um, wait a minute. No, then the impact will continue to hit my solar plexus. Just a long iron plate, about this height and width, should do. You can fold it and adjust it as you see fit."

"That's not how it works. No, ahem."

The blacksmith gave up thinking!

No matter how much he thought about it, it would only be embarrassing. And were there only few strange people among martial artists?

"Do you need it right away? If you just want me to make a steel plate, it will only take half a sichen. I'll make one for you right away."

"Ah, I would appreciate that."

And so, Qing obtained a steel plate!

She rented a room at an inn and spent a long time shaping the steel plate and trying it on her chest.

Finally, she was satisfied with the result.

First, she pressed down on the fat layer with a piece of cotton cloth, placed the gently bent steel plate on top, and then wrapped it again with cotton cloth to secure it in place.

When she put on he martial arts uniform, it didn't look too unnatural.

However, because the iron plate was pressed quite tightly, it stuck to his skin, making it very uncomfortable to wear.

Still, it was better than being in pain.

In fact, it was nothing more than insurance.

This was because Qing did not intend to attack the Five Poisons Sect.

\textit{If it were just the Five Poisons Sect, it would be fine, but the Blood Cult was involved, so who knows if it's just those poisoners or if other scum from other Blood Cults were mixed in.}

\textit{I already told my friends.}

\textit{The idea is to go ahead and monitor their movements and track them in case they run away or hide after realizing that their trickery through the plague has been exposed.}

\textit{Since Zhuge headed for the Diancang Sect, reinforcements will arrive soon, and in order to wipe them out, at least one of us must check on the Five Poisons Sect's movements.}

\textit{Of course, if it's just a bunch of poisoners and they seem easy to deal with, I don't need to wait for reinforcements and can just attack them myself.}

\textit{Basically, I just wanted to scout out the enemy.}

\textit{Of course, even though it was a selfish motive, I also had the ulterior motive of wanting to send my friends to safety.}

\textit{From the Diancang Sect's perspective, Zhuge was weak, and even if he was the eldest son of the Five Great Families from another region, they wouldn't want to harm a powerful heir, so they would not let him engage in battle.}

\textit{Yi-mei will stay with the Diancang Sect to take care of Ciyu.}

\textit{The guys who went to help Langzhong Daren can stay there and watch over the development of the medicine or do odd jobs.}

\textit{I'm sorry to the martial artists of the Diancang Sect.}

\textit{But I will fight alongside you with my transcendent sword, Harmony Heavenly Sword, and this neighborhood belongs to the Diancang Sect in the first place.}

\textit{If anything, they should be grateful to me. I have nothing to be sorry for. Yes, that's right.}

\textit{In any case, to at least make up for my guilt, I must gather as much information as possible while keeping a close eye on the enemy's movements.}

\textit{To do that, I must hide my location.}

\textit{But since I pared Zheng Liuzhang and that punk, the Blood Cult will surely be waiting for us on the way there.}

\textit{Well, it's been a while since I've been out and about.}

\textit{I could take the highway to the border, then head west and go straight through the mountains.}

\textit{It's the same straight-line maneuver I used when I went to Guangxi.}

However, the Blood Cult warriors may feel wronged.

They were tasked with finding the strongest bandit leader, Tudulian, and luring her out.

How could they have known that Tudulian would decide to pass through a primeval forest with no roads and not even a small village?