\chapter{Rice Blocks (17)}

Meanwhile, Qing understood why the Five Poisons Sect warriors wielded their weapons with their left hands.

The Five Poisons Sect warriors' left-handed weapons served as a kind of shield.

They wrapped their right hands around the weapons and swung them, releasing a pungent odor. This must be the poisonous weapon he had heard so much about.

Poison fists were inherently difficult to deal with.

Their power was far inferior to that of martial arts of the same level, but once hit, the poison seeped into the body.

\textit{But what is this body? Immune to all poisons.}

\textit{What is Myriad Poisons Immunity? Transcending Harmony Heavenly Blossom Sword.}

\textit{It is nothing special, I'm holding on with just muscle power!}

Suddenly, a palm strikes Qing's stomach violently!

Qing tensed her abs, and even though she knew it was coming, it still hurts.

But she endured it!

She could have dodged it, but right now, it's better to take the hit.

Why?

Since she's charging at her anyway, if she took the hit, he'll get more excited and keep hitting her.

It's much more difficult and annoying to deal with someone who kept creating distance and using mysterious footwork while throwing spear-like weapons.

A fierce battle ensued.

Qing's thighs, back, shoulders, stomach, and head were covered with deep wounds.

\textit{Ugh, what the hell is that just now?}

Qing responded in kind.

With the distance between them already narrowed, Moonlight Sword was planted firmly on the ground, two Buddhist Divine Art on the right and left hands: the golden-hued Tathagata's Divine Palm and the blood-red Great Handprint, were unleashed from a single person.

However, among the attacks, there were some that could not be blocked or withstood with just the body.

As if to prove that he was not just showing off, Huo Tianchi unleashed his Poison Palm.

"Die!" "No way!"

Poison Palm referred to the poisonous Qi emitted from the hands.

The palms collided with a loud bang!

The poisonous Qi dissolved in the Poison Palm flew in all directions, accompanied by a pungent smell, and smoke rose from the clothes that had been hit by the poisonous Qi, leaving holes in them.

In that moment, Qing put her strength into the palms that were pressed against each other and clenched his fingers tightly, entangling his hands.

\textit{I reall didn't want to lock fingers with a man.}

In an Inner Qi battle where you directly clash you inner strength, the most standard technique was to clasp palms together, as it was called "I-jung-soo-beop" in difficult terms.

Originally, she had planned to deal with the Sect Leader last, but the Five Poisons Sect were desperately clinging to her, hoping that the Sect Leader would deliver the final blow.

Even if she removed the poison, if she was hit with strong attacks, even someone as strong as Qing could have her bones broken.

So, she had to neutralize the Sect Leader first!

Qing raised her hand.

The moment sparks flew from Qing's eyes-

"Ugh!"

Qing's head was thrown back.

A strong hand grabbed her hair and pulled it, shaking it violently from side to side to distract Qing.

Seeing that they were entering into an Inner Qi battle, the elders resorted to a despicable trick to break Qing's concentration.

And it worked.

Her head was shaken violently from side to side, and at the same time, her head was slammed down and punched repeatedly with fists, so even someone as tough as Qing cannot help but lose focus.

Meanwhile, a sinister energy rushes from the palm of his hand.

It was the essence of poison!

It was a terrible poison that melted the meridians, blood vessels, muscles, and bones from within!

And the Gu parasite loved this poison!

In this state, an Internal Qi battle was impossible.

Qing clenched her fist tightly.

The strength of a woman known as the strongest in the land gripped Five Poisons Sect's Sect Leader's fingers tightly.

As those who have experienced it know, it was extremely painful.

"Kuh…"

But he endured!

Five Poisons Sect's Sect Leader let out a suppressed scream, his teeth grinding, but he didn't let go of his grip and pushes his poison into Qing.

But this was a mistake, as it ignored Qing's strength.

With a crack, the bones of Huo Tianci's fingers, caught between Qing's fingers, break, followed by—

"Kraaah!!"

With a heart-wrenching scream, the strength in his fingers, which had been clinging to Qing's hand, suddenly vanished.

Qing saw her chance and twisted harder, and only then did the two hands that had been clinging to each other separated.

However, Qing's fingers were still intertwined with Huo Tianchi's fingers, which had been separated from their owner.

With only his thumb left on his left hand and his little finger on his right, Huo Tianchi screamed and stumbled backward.

Meanwhile, Qing stretched both hands backward.

Qing's flexible body could stretch much farther than the average person can imagine.

In an instant, someone's head was in her hands.

Qing squeezed the head and felt around, "Ah, here are the eye sockets."

\textit{How dare this bastard grab someone else's hair? It's long and useless, just inconvenient, but still, it's my hair that Master cherishes!}

With the unique sensation of his fingers digging into the eyeball, a scream erupted.

However, the grip on the hair did not weaken at all, and even though her thumb was stuck in the eye socket, he held on tightly to the hair.

\textit{No, you still won't let go?}

Qing holds her thumbs in his eye sockets and exerted all her strength, as if to crush his skull.

The muscles in her upper arms, which were raised behind her back, bulge, and at the moment when his skull cannot withstand her grip, it cracked.

Huo Tianchi swung his hands, with one finger remaining on each palm, toward Qing.

Poisonous blood spattered from the torn flesh, splashing toward Qing's eyes.

The lukewarm poisonous blood rushesd into Qing's eyes, causing a burning sensation that was more intense than the poison itself.

"Aaah! My eyes, my eyes!"

In that instant, the elder's skull, which had been gripping Qing's hair, shattered, making her head feel lighter.

The spicy blood had entered Qing's eyes directly, and even she couldn't suppress her scream.

Something pierced Qing's mouth, which had opened wide from screaming.

"Kyaaahhh, gag, gag, gulp. Ah."

Without realizing it, she swallowed it. Anyway, whatever she swallowed wouldn't harm her, and whatever the poisoners fed her was obviously poison, but still she didn't know what she had eaten, making her feeelings extremely uneasy.

Qing's expression soured.

\textit{No, what the hell is this dog fight?}

In fact, desperation and dogfighting were similar.

A great man who has not yet been born said that life was a comedy when viewed from afar, but a tragedy when viewed up close.\footnote{Charlie Chaplin}

For the Five Poisons Sect followers, this was an infinitely desperate moment, but from a step back, it's hard to tell what kind of martial arts battle this is, and even mere bandits wouldn't do something like this.

The Five Poisons Sect followers were just clinging on.

They clung to her arms and legs, lashing out like enraged beasts, desperately trying to latched onto the Heavenly Flower Sword and stab her repeatedly with their poisoned needles and hidden weapons.

However, even with their hidden weapons, they couldn't pierce her armor, let alone her muscles, and could only leave shallow cuts on his skin.

So they cut the skin slightly and poured poison on it, then stuck poisoned hooks on top.

When the elders fell, they rushed in again.

Even if their heads were crushed, their arms and legs broken, or their ribs shattered, they rushed in again and threw themselves at her.

They cling to her so tightly that her arms and legs were bound like shackles, and even Qing, the strongest woman in the world, could only be dragged around and moved slowly.

Then, without fail, the poisonous arrows of Five Poisons Sect-ju Hoo-cheon-chi fly toward her.

Qing swung her arms.

With one old man hanging from her wrist and another from her elbow, she swung his arms, displaying a strength that could uproot a mountain.

"Guh!"

One elder was struck in the back by Huchonchi's poisonous fist.

He spit out blood, soaking Qing's front.

"Huff, huff. Ah, shit."

Qing's breathing was rough.

No matter how strong Qing was, how long had this battle been going on?

After first encountering Five Poisons Sect, she ran through the tropical rainforest with the sound of whistles ringing in her ears.

After that, she had completely surrendered herself to her martial arts and rampaged, slaughtering the soldiers of Daewol.

And now, here she was again.

"Shit, huh, a little!"

Qing roared and gathered all her inner strength.

Urrrgh! Urrrgh!

Purple lightning shot out from her entire body, striking Five Poison Sect's elders who were clinging to her.

Of course, it only had the of lightning, but in reality, it was a powerful striking technique.

If it had been real lightning, they would have been knocked down instantly, their eyes rolled back and their limbs torn apart, but unfortunately, it was only imitation lightning.

"Kraaah!" "Guh!" "Kuh!"

The air was filled with the sounds of people gasping for breath. The lightning tendrils struck their bodies, tearing flesh and breaking bones.

However, the elders clung to her limbs and held on.

"We'll help too, kuh, kuh!" "Everyone, kuh, rush… in! Bite her, drag her down!"

Even after a few elders was killed, the surviving members Five Poisons Sect clung at Qing.

Everyone was throwing themselves around, not so much to kill as to simply crush her down.

The Five Poisons Sect members piled on Qing like a mountain.

The mountain of people was shaking violently, and from a distance,  it was a sight that would make one click one's tongue and ask, 'What kind of fight is this?'

"Oh, come on!"

Qing, lying on the ground, pushed herself up with both arms.

Even with more than twenty Five Poisons Sect members on top of her, she managed to raise a mountain of flesh and blood as high as her arms could extend.

But it was only for a moment. With a thud, Qing was flattened back to the ground, grinding her teeth.

\textit{This must have been how Sun Wukong felt when he was trapped under the Five Elements Mountain.}

\textit{On the one hand, these guys are really vicious.}

More than half of the Five Poisons Sect disciples piled on top of Qing's body were already dead, and the rest were also destined to die soon.

They had been exposed to too much poison.

Even if they had already taken the antidote, they couldn't avoid poisoning if they ingested more poison than the antidote could neutralize.

On top of that, they had been repeatedly exposed to the poisonous fumes of Huo Tianchi, which, though incomplete, were still the vicious poison of a poisoner.

Yet they clung to each other, refusing to collapse even in death, their breaths faltering and fading away.

The mountain of corpses, the seal of death, was built by those who handled poison, dying by poison and piling up the bodies of others.

Below, two legs swaying towards Qing's field of vison, whose only had her head sticking out.

"Hehehe, tough, really tough…"

It was impossible to tell if he was crying or laughing, like someone sobbing, or a madman laughing silently, but it was clearly a voice filled with madness.

It was Five Poisons Sect's Sect Leader, Huo Tianchi.

Huo Tianchi was in a pitiful state.

Only one finger remained on each hand, and the silk clothes he was wearing were soaked in blood that their original color was unrecognizable.

The whites of his eyes were completely black, and black tears mixed with poison flowed from his eyes.

It wasn't just tears.

Black poisonous blood continued to flow from his ears, nose, and mouth, and anyone who saw him would know that he was already on the verge of death.

Even so, he staggered forward, one step at a time.

Then, he collapsed in front of Qing's head, and with trembling hands, he poured poison on her head, but that was all he could do.

The hand striking Qing's head had already lost all strength, barely managing to strike with the weight of the hand itself.

Pah, pah, pah.

The poisonous man kept striking the head.

It was a sight that others would fear to see.

A woman was lying under a pile of people, with only her head exposed.

In front of her, an old warrior sat down and silently struck her head.

\textit{Hmm, it hurts a little. More than that, it feels unpleasant…}

Qing's head was already as hard as iron.

How could it break under the blows of an old man who was so exhausted he could barely lift his own hands?

Huo Tianchi knew that too.

However, at the top of the head was the Baihui acupoint, the most vital point of the body.

He was just trying to strike it with his fist to poison the brain.

However, the poisonous blow to the head was gradually weakening with each strike.

Huo Tianchi was rapidly dying.

"Ugh, ugh, wait, ugh, hey. Sect Leader. Now, ugh, no, stop it. Are you going to crack my head open like that?"

Huo Tianchi raised his hand without answering.

No, he was trying to raise it.

His trembling hand slowly rose upward, but it couldn't reach the top and fell back down, hitting Qing's forehead with a thud.

Then he gasped for breath and asked.

"Ugh, ugh, why, why aren't you dead? Why, why do you look fine? Surely the poison, all that poison, seeped into you."

"Um, because the poison doesn't work?"

Huo Tianchi stared blankly at Qing.

"Not working? How? Even if you ate the antidote, no, this poison has no antidote, why, how?"

"Oh. I'm actually immune to all poisons."

"That's nonsense, there's no such thing."

"I'm right here, am I?"

Huo Tianchi's black eyes stared blankly at Qing.

"Poison doesn't affect me in the first place. Now that almost all Five Poisons Sect disciples are dead, how do you feel? Do your previous words still hold true?"

"What do you mean?"

"You said that you would sacrifice your life for revenge so that you could face your disciples in the afterlife. But you didn't even cause a speck of harm to your enemy. In fact, you caused me so much stings that I'd rather die from stings than poisons."

Qing continued.

"In any case, if you die without achieving even a speck of revenge, can you still face your end with dignity, as you said before? Oh, I'm not mocking you, I'm genuinely curious."

Huo Tianchi's lips trembled.

"It's so unfair. Truly, it's so unfair."

"Hmm. I knew it. You're just all talk after all."

At that moment.

Huo Tianchi murmured calmly.

"It's not about revenge. It's not about whether I can or cannot. It's because my strength, my martial arts, are insufficient. It's my fault, my incompetence. It's truly regrettable sin. I'm so sorry, this weak master, my disciples, my disciples…"

And then, he collapsed.

This was the end of the Sect Leader of Five Poisons Sect, and Five Poisons Sect itself.