\chapter{Rice Blocks (8)}

\textit{No matter how much I thought about it, there was no reason for Five Poisons Sect to find out.}

\textit{In the first place, the ones who survived facing the Tudulian were probably just a few who were spared on the mountain pass.}

\textit{The only one who I even pretended to have a conversation with was a guy whose eyes, ears, mouth, and hands were all crippled, completely cut off from communication with the outside world.}

\textit{The rest were just delivery men sent to die a horrible death because it would be a waste to let them starve to death, and a few remnants of the Blood Cult who were spared to pass on the name of 'the rice eater' and cause confusion.}

\textit{What possible connection could there be between Heavenly Blossom Sword and the strongest bandit, Tudulian?}

In fact, Qing made no mistake.

The enemy of the Blood Sect appeared, so Poison Demon sold Five Poisons Sect, who was worthless, in order to use them instead of his own men, who were worth saving.

So she was the victim of a baseless, ridiculous conspiracy.

That's why Qing felt wronged.

She even blamed herself, wondering if she had made a mistake.

Her heart sank.

\textit{Surely, you weren't standing here waiting to climb Mount Dazhai, right? But then, if my route up the mountain was even discovered, either the Blood Cult had already spied on me, or they'd already made some kind of thorough preparations…}

All kinds of doubts swirled in her mind.

"Ugh…"

While Qing was thinking, the Five Poisons Sect's member, who was still unable to breathe, struggled.

His palm of that touching Qing's hand on his throat moved violently, like a fish beating against a hook, as his lungs desperately try to push out the air, and Qing finally makes a decision.

\textit{First, retreat.}

\textit{Whether you know yourself well or your enemy well, you must first understand your enemy.}

\textit{Besides, I didn't come here to fight.}

\textit{My goal is to scout the Blood Sect—}

That was the moment.

Rustling! The sound of bushes rustling.

An old man suddenly appeared and raised a bottle of alcohol, saying,

"Disciples, are you doing your duty well? Would you like another drink?"

"Ah."

"There's a little left—hup."

The Five Poisons Sect Elder, who was sharing alcohol with his disciples, gasped in surprise.

He had returned all the way to the remote ambush site just to give his disciples (who had been left to take charge of the education of the disciples who had been killed in the massacre) another drink because there was some left.

The image of the disciples were rushing toward him with bright smiles, saying that the wine was very good. His heart was warm and his steps were light…

Unaware of his recklessness, he crept up quietly and what suddenly appeared before the elder's eyes—

The gruesome sight of one disciple's bodies split in half and the other one had their eyes rolling back in their sockets as they were grabbed by the neck and lifted into the air.

"Heavenly Blossom Sword…!"

The elder shouted and immediately lunged backward.

It was a technique known as a reverse charge, performed by leaping over the bushes he had just come from.

There was not even a moment's hesitation in his retreat.

Crack! That was the sound of a neck breaking.

With one hand, Qing easily snapped the neck of Five Poisons Sect's member and quickly stomped on the ground.

\textit{What the hell!?}

\textit{What the hell, at least say something, like you saw something you shouldn't have, and only then turn around and run away. You showed up calling up your disciple, so you should at least pretend to be angry, right?}

Qing felt very wronged.

What's more, she didn't even say anything this time!

She's wearing a bamboo hat, her lower face was covered in mud, and she even had metal plates pressed against her chest!

\textit{How did he recognized me at first glance?}

\textit{It's not like it says 'Heavenly Blossom Sword' written anywhere. Is it written somewhere? Heavenly Blossom Sword Ximen Qing?}

\textit{In any case, there can be no witnesses.}

\textit{Whether I kill him or capture him, the fact that I'm here must not reach the ears of the Blood Cult.}

The trees on either side of Qing's vision quickly passed by.

She moves her eyes quickly, using her heightened senses to read the terrain as best she can, moving left and right, sometimes jumping over obstacles, sometimes bending down low to pass under low-hanging branches.

Even in the tropical rainforest, where nature had created obstacles in all directions, her unrivaled Qinggong allowed her to move without hindrance.

However, the elder had aslo been wandering around the interior of the Ten-Sided Ambush formation for over half a month.

He was already familiar with the terrain, and his movements were so ingrained that there was no excess in his escape.

In contrast, Qing was completely new to this path.

Moreover it was the irregular ground of the forest, where the ground itself was unclear due to the thickets and fallen leaves.

Nevertheless, the distance between Qing and the elder gradually narrowed.

A martial artist who dabbled in the art of poison was objectively inferior in skill, and even the elder, without his poison, was embarrassingly weak.

Qing's right hand brushes the back of her head.

Before she knew it, she was holding a long skewer, a special combat pin made by Divine Maiden Sect.

Her right arm flashes upward, swinging wildly like a giant spear, and with a sharp whistling sound—

But it missed!

Almost simultaneously with the throw, the tip of the hairpin pierces the elder's thigh.

The hairpin, which had been about to stop on the knee, suddenly stuck into the thigh, either because Qing was stepping on a pothole or because the aim was off.

Still, it was a terrifying display of hidden weapon technique, as if the hairpin had skipped the process of flying through the air.

Of course, a master of hidden weapon techniques might say that it was just brute force and not a hidden weapon technique.

And it was not easy to hit the knee of a running opponent, as the lower body kept moving rapidly, even if the torso was immobilized…

Even though the hairpin was stuck deep into his thigh, the elder did not utter a single scream.

He continued to run, limping.

Is it because he wants to live that much, or was it because of the drug-like substance that surged through his mind at the moment of life and death?

If it weren't a time when he had to be caught and beaten, Qing would have tried to provoke him with words.

'What a pathetic old man, living a long life but still wanting to live a miserable life, exposing his back to his disciples' enemy.'

Thanks to the hairpin, the distance between her and the enemy quickly began to shrink.

One step becomes fifteen steps.

Another ten steps, and it's half a step away.

And five steps, now she can almost reach him with his sword.

Suddenly, the Heavenly Demon Qi burst out from Qing's dantian, kicking open the door.

The hatred that had been harbored for many years, now condensed into nothing but obsession, was the most tragic energy in the universe, even forgetting its original purpose.

The jagged flow scraped the meridians of her legs, causing a sharp pain that flowed to the Yongcheon blood vessel at the soles of her feet.

Then, bang! A different sound of footsteps.

Qing's new form stretched out like a thick stroke of a brush.

In an instant, she was close to his enemy's back.

The tip of her sword touches the enemy's back and pierced it smoothly, as if it were meant to be.

"Guh."

Qing swung her sword roughly.

The blade that had pierced the center of the back emerges from the side.

Coarse blood sprayed out into the bushes.

With a thud, the enemy fell to the ground, and Qing lands on the ground a beat later.

And then, just as she bent down to reach for the old man's trembling shoulders,

Squeak! Squeak! Squeak!

Whether it was the dying old man's last gasp or not, a loud whistle sound burst forth.

Qing quickly cut the elder throat, and the old man's head rolled halfway around, his eyes rolling as he looked at Qing.

Just before dying, the Five Poisons Sect Elder gazed at Qing, the enemy of his disciples.

The disciples who were buried in his heart were like children to the elderly elder, who had no wife or children, so you can imagine how devastating their loss was.

'How dare you, a mere child, presume to understand the pain of losing a child?'

'When the disciples who had gone to Sichuan returned with their heads pickled in salt, I too was already dead, so those you killed were not only my disciples but also me.'

'So why should I fear death?'

'I wish I had drawn you in deeper, but this is enough. Now, struggle in the crucible of blades I prepared for you until you die.'

'I will go to hell first and wait for you.'

If Qing could read his mind, she would be speechless.

'No, your disciples died while doing something wicked, trying to poison an innocent neighborhood and killing innocent people, and they were caught and killed.'

'If I were you, I would be too ashamed to even lift my head, let alone have children, after raising disciples like that.'

But the old man did not say anything and died as he was.

However, the old man's mouth twisted into a grimace, and the corners of his lips, which had been pursed, twisted into a crooked line.

A deep furrow appeared on Qing's forehead.

\textit{Why are you laughing?}

\textit{What is this?}

\textit{He ran away without even looking back, but now he suddenly has this grim determination, smiling smugly as if he's caught something…}

\textit{As if he's caught something…}

\textit{Ah, shit.}

\textit{He didn't run away to save himself, but to lure me into chasing him.}

-Peeek, piiik, piiii.

-Piiik! Piiik! Piiik!

-Piiik, piiik! Piiik! Piiik!

In response, the sound of flutes came from all directions at once.

Pee-ee… Pa-bang.

Even the sound of firecrackers exploded on the trees' canopy.

Qing took a deep breath.

\textit{This time, I was really, realyy going to wait quietly and just scout around.}

\textit{These poisonous bastards, they want to use poisons that doesn't even work on me?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was a lazy evening during a grueling ambush operation, but a glass of clear liquor warmed their stomach.

Pee-eeek, pee-eeek, pee-eeek…!

A violent sound tore through the lazy atmosphere.

Hou Tianchi jumped to his feet.

There was no set signal for when the enemy was spotted, when that despicable enemy was discovered.

Because no matter who blew the whistle loudly, it was a signal that the enemy had arrived, that the hated Heavenly Blossom Sword had arrived.

Since nothing else was expected except for the Heavenly Blossom Sword's pursuit, there was no need to set a specific signal for her discovery.

There was no need to number or classify a single enemy, so just blowing the whistle was enough for the first signal.

The sounds of the whisle continued.

This time, the flute sounds were the regular signals.

Confirmed, 40th unit, enemy presence detected, preparing.

Confirmed, 41th unit, preparing.

Confirmed, 38th…

Confirmed…

The whistle sounds spread rapidly.

Just by listening to the sounds, Huchonchi could imagine the start of a Ten-Sided Ambush formation filling the left and right sides of a huge circular area.

Then, pip, bang…! Bang…! Bang…!

It was the signal that the core of the formation had been set.

Huchonchi counted the number of firework signals.

One, two, three… six, seven.

Eight!

Cheonmang Yoksam Munbongsa Jin, the 64-door seal formation.

It divides the eight directions into eight sections, with only one of the 64 doors being the gate of life (the exit), and even that continues to change and move.

Despite its grand name, its only effect was to twist the direction and trap the enemy so they cannot escape.

However, simplicity was the ultimate perfection.

Unlike other infamous techniques, which have extreme distortions and hallucinatory effects that can be seen, heard, smelled, and touched, this technique focuses all its power on simply confusing the enemy.

However, various deadly traps were added to it.

And if you combine that with a large number of soldiers who have mastered the changes in the technique and the resulting movement patterns?

Heavenly Flower Sword was nothing more than a novice.

Even if someone were to reach the realm of Hwa-gyeong through such an unbelievable achievement, it would make no difference.

No, even if they reached the realm of Profound Realm, it would be the same.

In such a trap, even a master of the Life-and-Death Realm could be killed.

If poison was used, even a master of the Celestial Realm can only grasp the poison and delay it, and then take time to detoxify it later.

Therefore, if you continue to pour poison over and over, even a master of Mystical Realm cannot survive.

Of course, to even capture a master of the Profound realm, one must be prepared to lose almost all of one's disciples.

Five Poisons Sect had already made up its mind to lose most of its disciples.

Now that they have joined hands with the Blood Sect, the downfall of the sect was inevitable, whether it comes soon or later.

\textit{However, if I do not avenge my family and my disciples, what is the point of the sect existing?}

Huchangchi's expression contorted.

He looks like he was crying, like he was angry, but he was smiling wildly, filled with those emotions.

\textit{Heavenly Flower Sword, that bitch, will die today.}

What kind of nonsense was this? It's the kind of absurd story that only appeared in the tales of idle nobles—

Indeed, unless one has attained the realm of Myriad Poisons Immunity.