\chapter{Rice Blocks (10)}

Tsk, Qing spits out all the salty saliva in his mouth.

A cold fire freezes inside his chest, and a sharp heat rises.

Fanning the flames were the Five Poisons Sect men, who have stopped their attack as if to say, "Well, how was it?"

You're trapped, so what now? What were you going to do? Whether you run away or fight back, go ahead and try, as if daring him to do so.

Qing's guess was half right and half wrong.

The enemy of his sect wanted to chase him down and torment him slowly, just as Qing had expected.

The reason was that the Oedokmun sect firmly believed that time was on their side.

They figured that since they were already quite poisoned, they just needed to keep tracking them and not give them time to detoxify.

However, Qing's anger was growing.

These insignificant creatures, with nothing left but their cruelty, trampling on the corpses of their comrades, clinging to evil, believing that someday their chance will come?

Anything can be achieved with willpower, determination, and unyielding tenacity? You can overcome anything with evil and stubbornness?

Are you really going to fight with such desperate determination, ready to die?

Okay, then.

Let's see how strong your determination really is.

What breaks strong will was an even greater shock.

You call yourselves the best, but you think people were so easy to defeat.

You didn't even beg for your life, promising to live a good life from now on, with your hands and feet worn out from begging.

Those who tried to massacre innocent people, what did they do right? Their offspring were holding their heads high, calling them enemies.

Huh, Qing takes a deep breath.

Alright, let's give it a try.

Qing returns the Moonlight Sword to its sheath.

Then he steps on the shoulder of the meat shield and grabs his wrist, pulling him toward him.

The skin stretches and tears, revealing the severed arm of Five Poisons Sect-do in his hand.

Then he shouts loudly.

"I am not the Heavenly Flower Sword! I am not! The Heavenly Flower Sword uses a sword, but I use my arm!"

The atmosphere suddenly becomes tense.

Qing's lips twist viciously.

Who decided to be so dramatic?

If you insist on acting this way, I will do the opposite. I will give these worthless bastards a very funny, no, not even funny, end.

"My name was Dodokryeon! I am a righteous bandit!"

I will not fight you seriously.

I will make even your deaths ridiculous, consumed as someone's joke, unbearably trivial.

The scoundrel of the world continues.

"And tonight, I will steal the lives of you villains! If you surrender your lives willingly, I will spare your lives!"

Qing's waist bends slightly, but he moves gracefully without any rough footsteps.

His movements were slow and elegant, like a beautiful woman out for a stroll.

However, he was holding someone's arm.

He doesn't seem to be targeting anyone in particular.

After all, it seemed as if Five Poisons Sect's men were already spread out in all directions, so if he ran anywhere, one of them would surely be startled and jump out.

Sure enough, the upper body of an Five Poisons Sect soldier appeared from behind the bushes.

What? Did they dig a trench?

The expression on the Five Poisons Sect's face when he saw Qing changed from fear to hatred, and then to a grim determination.

I don't like these three changes at all.

The Five Poisons Sect hurriedly took out a tube and aimed it.

The muzzle of the tube formed a perfect circle in Qing's field of vision.

If it had eyes, they would have met directly. How dare he aim a gun at a person's face?

Five Poisons Sectdo pulls hard on the string attached to the back of the gun, which looks like a large firecracker.

Qing speeds up and runs forward.

Then he roughly extends his palm, wrapped in a pale blue aura, to block the muzzle of the gun—

Bang! An explosion echoes, and gunpowder smoke spreads.

At the same time, a voice filled with laughter and mockery rings out.

"This was a bulletproof palm! Where were you going?"

Boom! A terrifying sound of shattering glass!

The arm wielding the meat shield like a club. Its tattered upper arm strikes the cheek of his fellow disciple with great force.

Slap! An indescribable, crisp sound of impact, the unique sound of wet flesh colliding with flesh. It was an arm wielded purely with strength, without any internal power.

The teeth of the Five Poisons Sect-do begin to fall out en masse into the wide world.

As he strikes, his arm was bent sharply to the opposite side, revealing a face covered in blood, with teeth as white as snow.

"It would be strange if only one tooth was left, wouldn't it?"

"Ah, no…"

"Yes."

Qing's upper arm bulged slightly.

A slap was meant to be delivered once when it comes and once when it goes, twice in one breath.

Slap! Another intense sound of a spear piercing the air.

Qing turned around, grabbed the meat shield's wrist with both hands, and swung it with a big motion like a baseball player hitting a ball.

Thwack!

The spear collided with the meat club, and the force behind it instantly tore the flesh from the club.

In an instant, only the bones remained above the elbow, leaving nothing but flesh and bone.

Unfortunately, behind him, Five Poisons Sectdo had dug into the ground and was leaning forward, and he was hit by the flying flesh, as if he were a baseball player catching a ball.

Five Poisons Sectdo slapped his face, the pain from the flesh stinging his skin, and his eyes flashed with fierce hatred.

Then he thrust his hand into his sleeve.

"Where!"

Qing's left foot shot backward.

It was a powerful back kick, as if drawn from a picture.

Qing's foot struck his opponent's face.

His nose breaks instantly, followed by the collapse of his facial bones, and the sole of his foot digs three knuckles deep into the center of his face.

Then, a massive burst of energy explodes from the center of his foot.

The body of the Five Poisons Sect-do, with only his lower half remaining, falls backward and comes to rest against the wall of the dojo.

The leaning corpse drops its arms limply.

Thud. A fairly large pouch falls from the sleeve and lands on the floor, tearing open slightly.

At the same time, there was a loud bang!

It sounds like fireworks going off, but suddenly, a red cloud explodes!

What was this, a poison pouch? I have one of these too. Hmm, do all poison masters use similar methods?

Poison masters might feel wronged if they heard this.

So, does that mean all martial arts schools use similar weapons because they're all similar?

Poisonous smoke swirls around in an instant!

An ordinary warrior would be terrified and try to retreat as quickly as possible, but Qing was no ordinary warrior.

What was that, poisonous smoke?

Poison was completely harmless to me—

"Gah! Ugh, ugh, ugh…!

Qing let out a scream.

The poison had no effect on Qing; instead, it was a delicious treat that compensated for the lack of spiciness in Zhongyuan.

So, "spicy."

In an instant, the pungent spiciness penetrated his eyes, nostrils, and all the sensitive mucous membranes inside his nasal cavity!

Of course, Go Su-eun's eyes were a little stinging, but she couldn't open them. The problem was the burning sensation in her nose, as if she had swallowed the spicy soup and it had flowed back up her nostrils!

"Kkak! Kkak! Gak!"

It would be easier to endure if there were a hole somewhere in my body, but the spiciness permeating my nasal cavity makes it impossible to suppress the screams.

Meanwhile, Elder Five Poisons Sect, holding a spear, smiles savagely somewhere between the agonizing screams and retching sounds reaching his ears.

"Look, the poison was working! Children of O-Dok-Mun! Listen, these were the screams of your enemies!"

The elder shouts loudly, then suddenly stops.

But did he really give them a poison that would make them scream so instantly? Surely the poison smoke rising was a delayed-action poison that scattered their internal energy?

At that moment, the enemy bursts out through the poisonous smoke.

The elder hurriedly pulls back his spear.

At the same time, the horn sounds, signaling that the target was fleeing and the poison was taking effect, and to continue pursuing and cornering him.

As the horn signal spreads, the elder rushes toward the direction where Qing disappeared.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tears stream down, snot flows endlessly.

The only fortunate thing was that the target had already covered his face with mud and was covered in blood.

No matter how much tears and snot flowed, it didn't show on the surface, so at least he avoided looking pitiful.

The unfortunate part was that even if she wiped away the tears and snot, she was already covered in mud and blood, making her look terrible.

Her white eyes were bloodshot.

I will never forgive these bastards.

Every time I breathe, the inside of my nose stings, and the inside of my head feels hot and painful.

It's not painful, just a burning sensation, but

it feels absolutely awful.

"Aaah!"

A loud sound escapes my mouth.

If you've ever had spicy soup and it went down the wrong way, you know how unbearable it is.

Beep! Beep!

A loud whistle.

Qing's eyes turn into axes.

Bang! The poor man's skin bursts open as he charges forward!

Then, there was a loud sound like a metal container bursting.

Qing crosses his arms in front of his face to block the blow, then pulls out the large sword he had dropped earlier and swings it fiercely.

At that moment, there was a loud clang!

The heavy weapon flies quickly and strikes the blade of the moonlight sword.

The blade, which should have pierced the top of the head, was deflected to the side, slicing off a chunk of flesh from Five Poisons Sectdo's shoulder before embedding itself in the dirt.

"Die, enemy!"

Despite his shoulder being sliced open to the bone, Five Poisons Sectdo reaches out with his remaining hand and thrusts forward with his dagger.

The tip of the dagger pierces Qing's side.

A finger was pierced by the dagger.

However, O-dok-mun clenches his teeth.

He knows that there were no bones in the side, so pressing down will only push it in, and it will only pierce the flesh slightly because it was blocked by muscle.

O-dok-mun-do grits his teeth in pain.

If only my skill had been a little higher, if only I had been more skilled with the sword, if only I had dug in a little deeper and let the poison flow…

That was O-dok-mun-do's last thought.

This was because people usually cannot think when the top of their head was dented.

Qing, who had turned Five Poisons Sectdo's head into a concave shape with his weapon, withdrew his elbow.

A true master, no, no, what kind of master was a supreme master? There were many real masters here, but these brats were just throwing daggers from a distance.

Because of that guy's lightness technique, his unpredictable movements left and right, and the dense trees, it was impossible to catch up with those low-level guys.

Come to think of it, was that Five Poisons Sect's power?

He escaped in an amazing way, threw daggers from afar, and when I chased after him, he ran away again. He's completely invincible.

Is Five Poisons Sect not to be underestimated?

It was a complete misunderstanding.

Of course, Five Poisons Sect was also completely misunderstanding Qing.

He must have been poisoned by all kinds of toxins and poisons, so now he can't even talk as much as he used to.

It's just that Qing's nose was so sore that he couldn't speak.

On top of that, just when things were getting better, that bastard started smoking again.

Just like now. Puh!

"Kyaaah! Again!"

Sometimes, even when your head was down, you can still think.

The hatred that has seeped into your very marrow, even when your head was down and your brain was mushy, works miracles in the last moments of your life, pulling the fuse of poison and killing you.

Qing's tears won't stop flowing.

The snot flows like a waterfall, and I keep wiping it away, thinking it might turn my nose red and raw.

But more than that, as I kill each of the sneaky O-dok-mun-do one by one, a big question keeps lingering in my mind.

The Five Poisons Sect-do do not flee, even when given space.

At the moment when they should charge, when they were already caught and have nowhere to go, they charge forward with burning hatred, even knowing it was a certain death.

Why?

Why do these creatures go to such lengths?
