\chapter{Rice Blocks (14)}

A woman stands alone among the bodies strewn about in a gruesome state.

Her face was covered in dirt, and red blood still flows from it. Below, dried blood and pieces of flesh were stuck to her, making her look like a monster.

The woman looked around with a cold gaze, then suddenly opened her mouth and muttered.

"I'm hungry."

It was about time she was hungry.

The sun was slowly setting, and the sky was red. She had been running, flying, and fighting with a knife for an hour and a half, so she must have been exhausted.

And Qing usually eats four meals a day.

Breakfast, lunch, dinner, and a late-night snack, plus snacks in between.

Part of it was because she has a big appetite due to her past experiences with food, but

the side effects of the Jinju family's study method, which was designed to nurture one's innate potential, were significant.

In any case, I'm hungry…

"Hmm. Let's find something to eat."

Qing quickly moves forward.

He searches among the bodies of Daewook soldiers lying everywhere, lifting tents that were still intact and looking inside to see if there was a kitchen or some rice left over.

However, what was the condition of the items he finds?

Gold, porcelain, blood-stained silk clothes, ink and inkstones, silver and copper coins…

Did the Daewook soldiers buy souvenirs while they were in Zhongyuan?

No, that can't be.

There was only one thing that soldiers from another country would do when they entered a foreign land, and that was to loot.

This had been the case for a long time in Zhongyuan, and indeed, it was the norm in this era. From the past to the present, looting was considered a natural and legitimate right of the invaders.

When you invade a foreign country, you loot.

This was so natural and normal that no one tried to stop it.

Even those who were being plundered know that this was to be expected, so they don't even bother to fortify their villages or buildings.

Having no interest in the blood-stained goods, the Qing soldiers stopped rummaging through the tents and campgrounds.

In the Qing soldier's hand was a small piece of jewelry, a headdress that would have been worn by a girl of his age.

There were traces of blood and dried blood on the end.

Hmm. What a bunch of bastards.

I should have killed them all instead of letting them escape.

Anyway, with all the vicious traps scattered throughout the tropical forest, I thought they would die on their own if I left them there.

But I was getting a little tired.

And there was no reason to go back into the tropical rainforest.

If they were after me, it would be better to wait in an open field with no trees to block the sky and no obstacles.

Hmm, if it's a military camp, they must have stockpiled water and food somewhere. Ah, here it is.

Qing first scooped a large ladleful from the water container, and for a moment, the intense cold of the ice water swept over him. He quickly brought it to his mouth.

The cold water was refreshing after inhaling the acrid smoke, and his dry throat felt like it was being washed away. Wow, this was heaven.

How could the people of Jungwon not appreciate the beauty of cold water?

After moistening his throat, Qing scooped up another bucket of water and poured it into his nose.

With a "gurgle," the water that went into his nose came back out of his mouth, and the amount was enough to rival a waterfall.

Phew, that's better.

The inside of my nose was still stinging, but I can live with that.

After rinsing his nose, Qing began searching the food storage area in earnest.

Dried bread. This must be Daewol's combat rations. Yum, it tastes awful… Chew, chew. Still, as he chews, he thinks, Hmm, it's tasteless.

Even so, he picks up a piece of bread and continues to chew it while opening the box.

Salted meat. What kind of meat was this? Still, they're Daewol's soldiers, so they wouldn't eat strange meat.

Is this rice? Ah, it's long-grain rice.

Oh, salt. What's this? Some kind of Daewoo spice?

This is… hmm, incense, coriander.

After looking around, he got a general idea of the layout.

Next to the food storage room was, of course, the kitchen.

I gather some firewood, light a fire, put a large pot on it, pour water into it, and throw in all the ingredients.

People who know good food well can make something that tastes pretty good even if they just throw everything in haphazardly.

Besides, it's hard to make something that tastes bad when you boil meat, rice, and spices together.

Gradually, the aroma of something delicious begins to waft through the air.

Qing finds herself humming a tune without even realizing it.

Ah, if only I could take a refreshing shower before the rice was done and then soak my body in the boiling hot water—that would be pure heaven.

And then, when it comes out fluffy and soft, and you eat the porridge that has been simmered for a long time, wow, that's just heaven, isn't it?

Qing stares blankly at the fire under the iron pot, lost in thought.

In Qing's hometown, they call this "fire gazing."

Ah. I want to wash. I'm covered in dirt, it's sticky and dirty, and I haven't washed my hair in ages, but washing my hair was such a hassle. Why did my hair have to grow so long? It's not just washing, I have to scrub it, and it takes forever to dry…

Meanwhile, the water was boiling.

I guess I could eat now, but should I?

No, the rice needs to release some of its starch and thicken a little so that it sticks to the bottom and tastes better.

Right now, I just want rice soup. Yes, rice soup.

Qing's gaze shifts from the fire to the rice.

He stares at the rice and swallows hard.

Now he wasn't staring at the fire, but at the porridge.

How much time had passed?

The boiling water turned into bubbling porridge, gradually rising with a dull popping sound.

Okay, I think I can eat now.

Qing smiled more brightly than ever before.

Even so, it looked like a beggar, a real beggar, but perhaps that made it look more realistic.

And finally, when he lifted the spoon (extra large) he had hastily carved from a bed leg—

Pik, pik! Pik pik pik pik!

-The Heavenly Sword was in here!

-Throw away all the remaining poison!

Then, from far away, there was a sound of something falling, followed by things pouring into the entrance of the tent.

Qing's face contorts.

"No, damn it, I haven't even taken a bite yet—"

Tada-dang, pushi-shi, bang, clang, clang.

The sound of poison pouches bursting and smoke escaping, the sound of poison bottles shattering and the poison vaporizing, and the sound of poison bullets exploding.

In an instant, the tent was filled with thick, choking poisonous smoke.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

O Dokmunju Huchonchi quietly opened his eyes.

Huchonchi looks quite terrible.

The veins throughout his body were black and bulging, and the whites of his eyes were also black, making him look hideous.

An incomplete poisoner, a half-baked poisoner, had drawn up his poison and was ready to face his enemy.

Having achieved a level he couldn't reach on his own through underhanded means, he would naturally have to pay a heavy price to wield his full power.

Especially if that power was poison.

And Huchonchi was already prepared to pay that price.

With a determination that would cost him his life, Huchonchi asked solemnly.

"That woman? Did you drive her in? What were you doing?"

This moment was the last moment of despair for Heavenly Blossom Sword.

He had bought some time.

So he tried his best to remove the poison from his body.

Even a master becomes vulnerable when trying to control poison.

Even so, what must it be like to try to remove the poison in the middle of enemy territory?

His heart must be pounding as if the enemy were about to attack at any moment, his insides burning with anxiety and impatience.

And with a glimmer of hope that they can drive out the poison and escape, they would try to restore their poisoned bodies by any means necessary.

Unaware that the disciples and elders of the Odo Gate were gathering around the camp of the Moon Country barbarians.

Then, seeing enemies blocking their path in every direction, they would despair.

Perhaps they will beg for their lives.

Huchonchi flashes a cruel smile.

However, the disciples hesitate for a moment.

"Um, Master. That is…"

"What were you doing? This was wartime. Where was there time to hesitate?"

The commander rebukes the disciples.

At his urging, Mun-do opens his mouth with difficulty.

"That is, the Cheonhwa Sword was now…"

"Now?"

"I'm cooking rice…"

"What!?" "What!?"

Huchonchi and the commander shout at the same time.

"What were you talking about? Rice? You should be quietly calming yourself down and controlling your anger, and you're cooking rice?"

"Yes, smoke was rising, and according to reports, it smells quite delicious…"

Huchonchi and the commander's expressions simultaneously contort.

Is she out of her mind?

We don't have a moment to spare to get the poison out of our bodies, and she's cooking rice?

If she was really hungry, she could have just quickly eaten some tasteless military rations, but she's cooking rice? It smells delicious?

This woman was mocking us to the very end.

A stream of ominous poison flows from Huchonchi's eyes.

This was not a metaphorical expression of anger, but actual poison flowing out like mist.

Huchonchi was a poisoner.

"Cough, ugh."

"Lord Moon."

When a low-level disciple coughs from the poisonous gas, the chief officer cautiously restrains Huchonchi.

Huchonchi takes a deep breath.

"I was going to give you a little time to get your affairs in order, but it won't work. Get ready immediately."

The disciples surrounding the open space begin to project the remaining poison at once.

The disciples, whose skills were still low, could only throw as far as they could.

The elders threw their poison in a stunning arc toward the entrance of the tent in the distance, where smoke was rising.

As a result, thick poisonous smoke covered the entire camp.

Huchonchi looked at the poisonous smoke rising into the sky.

Just as smoke drives beasts out of their dens, that damn woman will soon burst out from somewhere.

But now that the elders have surrounded her, I will end this long feud myself.

Huchonchi's eyes flash.

Yes, what should we do with her corpse?

If I display her naked body, she will be forever shamed in history even after death. Or perhaps I should pickle her body and send it to the shrine of the goddess…

Huchonchi continues to ponder joyfully over how to dispose of the corpse of Heavenly Blossom Sword.

Or perhaps I could stretch out her skin and make a bed, hang her head above it, or maybe a footstool would be better, or even worse, I could find a more disgusting use for her…

His contemplation continues.

Continue.

Chuuk.

Chuuk.

Huchonchi, who had been smiling slyly, suddenly felt uneasy.

How long had he been lost in thought?

"…What about Heavenly Blossom Sword?"

"There was no news."

"Are you sure Heavenly Blossom Sword was in there?"

"Yes, he hasn't been seen since he entered the tent. I'm sure."

"But then, damn it!"

Huchonchi's heart sank.

Could she already be dead?

Preparing a meal… I realize that I've already failed, so I'll enjoy my last meal… No, I can't! I mustn't!

"I told you not to use such strong poison!"

"Master Mun? The only poisons used in smoke signals were either San Gong-dok or Ji Yeon-seong."

"Damn it! Did I overestimate that woman?"

Huchonchi shouted and hurriedly walked toward the Daewolguk campsite, where the poisonous fumes had not yet dissipated.

I can't die! If I die, it must be by the hands of our Daeodokmun! I can't die alone from such poison!

"Master! Brother! Oh no, the elders!"

The commander hurriedly followed Huchonchi, and then, accompanied by the sound of whistles, the elders gathered in a circle around them.

And then, the army tent of Daewolguk.

The elders of the Five Poisons Sect clan surround the tent, which was still filled with thick poisonous smoke, and simultaneously strike the pillars, breaking them.

With a loud crack, all the pillars break, and the tent collapses, billowing outward in all directions before crashing down.

Poisonous smoke gushes fiercely from the entrance.

In an instant, crimson energy flashes, crossing in a net-like pattern.

Starlight pierces the tent.

Between the gaping holes in the collapsing tent, a figure appears.

Finally, it was the moment when Huchonchi faced the Heavenly Sword.

However, there was a pot of rice porridge beside him.

"Wah, mmm, hot, mmm, huh, mmm, gulp. Wah, mmm. Huh, huh, hot."

Hugging the large pot wedged between his sides, he hurriedly moved the spoon as if guarding it from someone trying to take it away.

It was the sight of the Heavenly Flower Sword greedily scooping up rice porridge.
