\chapter{Rice Blocks (13)}

In fact, the army of Zhongyuan was known to be the weakest.

The individual abilities of the soldiers were lacking, and no matter how you try to sugarcoat it, the military discipline was in a terrible state.

Furthermore, the soldiers were more concerned with their own safety than with the collective good, so when they encounter a formidable enemy, they panic and break ranks, each fleeing for their own survival.

It was truly a disorganized and chaotic army.

If there was one thing they were good at, it was farming.

When it comes to farming, they were unmatched by any army in the world, with farmers who were as skilled as a hundred soldiers.

One might ask why this was an advantage.

Why should skilled farmers be an advantage for an army, which should be composed of combat experts?

However, this was an incredible advantage.

This was because the army can be left alone to farm and feed itself.

The extremely low maintenance costs of the army were the source of its strength.

These low maintenance costs,

combined with the vast land and overwhelming population, resulted in an army numbering at least ten thousand.

This was the secret behind how Zhongyuan army, despite being practically the weakest in the world, became the strongest army in the world and supported the emperor's rule.

Conversely,

the countries near Zhongyuan, or the so-called barbarians, had to defend themselves against this powerful (though not necessarily strong) army with a small number of troops.

Therefore, the barbarian armies were basically strong armies.

The soldiers of Daewoo were also strong soldiers who were well fed and carefully trained by the King of Daewoo.

As soldiers who were raised in a country, their loyalty was naturally sky-high.

No evil vampire could defeat the regular soldiers of Daewoo!

"Die, bloodsuckers!"

Golden armor, or more accurately, golden silk covered over a double-layered armor.

Thanks to this, Qing realized that the bloodsuckers pronounced Daewoo as "makaron."

Normally, Qing would have thought, "Now that I hear it, I want to eat it," but

But now was the time when the demons were rampaging.

And there were enemies right in front of him?

Qing's clown face rose again.

Bang! Qing's new technique was fired in an instant.

His right arm, which had been stretched out behind his left side, spread out at a fierce speed.

The moonlight sword that followed drew a crimson line that seemed to split the space itself.

"[General!]" "[I'll help!]"

Following the trajectory of the moonlight sword, seven crescent blades simultaneously pierced the air in a reverse fan shape.

Kaang! The seven crescent blades flew off at once.

However, the crescent swords, which had drawn a graceful circle, return, wrapped in a dark blue aura.

The barbarians know very well that they do not fear the soldiers of Zhongyuan.

What they fear was the countless number of soldiers, which were as numerous as grains of sand, and the even greater number of cannons.

And if there was anyone the barbarians feared, it was the martial artists.

In the eyes of the barbarians, the emperor of Zhongyuan was a completely insane person.

Wouldn't he let individuals with enormous power run free without any restrictions from the laws of the country?

For the barbarians, martial arts were the exclusive property of the army and the ruling class, so they could not understand the free practice of martial arts in Zhongyuan.

Of course, the emperors could feel wronged.

With such a vast land and martial arts spreading so widely, how could they possibly control it?

There was a time when they were used as quasi-public officials to govern the provinces, but then some ignorant fool came along and grabbed them by the scruff of the neck, and now look at them.

And national law?

The martial artists don't obey the law!

In any case, to barbarians who don't understand the situation, martial artists, or more precisely, martial artists who were masters of their art, were the most troublesome people there are.

Therefore, the Daewoo military has long studied ways to deal with martial artists and trained intensively in practical combat.

The Daewoo military's martial arts techniques for defeating martial artists!

And now, the results were on display!

Seven crescent swords dance together as if wielded by a single person.

Kang! The sound of one against seven colliding echoed as one, showing just how precise their coordination was.

In an instant, the seven warriors of Daewol stepped back in unison.

To absorb the impact of the crescent swords.

The general's eyes tremble.

What kind of power was this?

How can seven warriors be pushed back by a single sword?

Is this really a demon, a vampire?

A wicked smile appears on the vampire's face.

It was a hideous and terrifying smile, one that made it impossible to believe that a creature of this world could smile like that.

At that moment, the elite soldiers instantly entered battle formation, their spear tips piercing in from all directions.

Suddenly, a purple lightning bolt flashed!

A moment later, a thunderous roar split the air, tearing through the space with a fierce roar.

The soldiers who had been charging forward were thrown back.

In an instant, the vampire's head whipped around.

The general turned his head and saw soldiers charging forward with a chariot in front of them.

The vampire's eyes flash.

"No!"

"Yes."

The vampire splits into eight.

Some jump high, some run on all fours like beasts, and some advance with unnatural flickering movements.

The general grits his teeth.

What a monster! This was the kind of magic only a monster would use! What on earth did those Zhongyuan people pass on to us?

"Damn it, soldiers, the vampires! Over there! The monsters were targeting the soldiers!"

But it was already too late.

One of the eight translucent vampires split into two and revealed its true form on top of the cart that the soldiers were pushing.

And then there was blood.

"Vampires, vampires!" "Die, monsters!"

The vampires swept through the area.

The huge blade it wields was monstrously cruel, as one would expect from a monster.

It chops the soldiers into pieces.

Its left arm flashes upward, revealing a huge, twisted palm, which it swings down, instantly decapitating a soldier.

The soldier's body collapses.

The vampire snatches the soldier's crescent sword and stomps roughly on the ground before leaping high into the sky.

"Now's our chance! Throw the net!"

"HwaQing, where were you?"

Historically, nets have been the most effective weapon against strong individuals.

Well-trained soldiers throw nets toward the vampire's flight path even in the midst of this massacre.

They do so, hoping that the vampire will jump into the net.

However.

The vampire stops in midair.

Not just stopping, but sitting crouched upside down.

"It's a real vampire! It's flying! Eeek!"

"But… it didn't put its toes in its nostrils! How was that possible?"

For reference, it was said that the yokai Makaron of Daewookguk can only fly by holding both earlobes with its hands and blocking its nostrils with its big toes.

Unless you were from Daewol Kingdom, it was impossible to understand why a monster that flies around in the shape of a human being, with both hands covering its ears and both feet covering its nostrils, was so terrifying.

Isn't that funny?

The people of Daewol Kingdom would argue.

Then, what was flying around in the shape of a person, covering both ears with both hands and both nostrils with both feet, and why isn't that scary?

Suddenly, a vampire sitting upside down in midair stretches its legs and falls down.

The net cuts through the air, and not only that, it covers and crushes several soldiers.

However, the soldiers crushed by the net were lucky.

Boom! The ground caves in, and the soldiers were thrown out like broken dolls, rolling on the ground.

Wee-eek! Some spit blood, while others scream in agony, clutching broken arms or legs.

And at the center of it all, a vampire kneels with one knee on the ground and one arm braced against the floor, raising its head suddenly.

"[Ugh! Die!]"

"This monster, dare to attack Won-joon-mo!"

They say that soldiers become true soldiers when they lose a comrade.

Soldiers who have lost their friends, colleagues, and comrades were filled with rage and thrust their spears and crescent swords.

However, the vampire stands up and crosses his arms over his head.

Kagagakang! The crescent swords strike the vampire's forearms, making a loud clanging sound.

Numerous spears pierce the vampire's torso, which was raised with both arms.

"Eh, eh…?"

"The spears aren't going in! Monster!"

The soldiers wielding spears were foot soldiers who have not yet mastered the martial arts of the military.

Only after training to develop the minimum strength and stamina required to wield heavy weapons can they wield crescent swords.

Seeing this, the general sighs.

The lower-ranking soldiers' strength was not enough to pierce the monster's skin. How can such a terrible monster exist?

"[Senior soldiers! We must stop them! Vampire! Your opponent was here!]"

The general shouts loudly and leads the elite soldiers, the senior soldiers, to the front.

Then the vampire also shouts.

"I am not a vampire! I am the strongest bandit, the rice-eating bandit, Dokryeon!"

"Die, vampire!"

"Dokryeon!"

The vampire charges at the general again.

However, the seven warriors of Daewol have already observed the tactics of the enemy, the vampire, and Dokryeon.

They can split into eight and move like illusions, but they can track where the vampire's gaze was directed.

They leap high into the sky at an incredible speed, but suddenly flip in mid-air, change direction, and plummet down.

…How on earth were we supposed to deal with this?

But they can't just run away.

For the sake of our great homeland, for the glory of our people, and to repay the grace of the great Daewang.

"Let's go! For His Majesty!"

"For His Majesty!"

The general shouts in high spirits and rushes forward.

The six generals follow behind him.

Each of them repeats the conclusions they have drawn from their previous encounters and the slaughter of the monsters.

The swing of the giant sword was as powerful as its size, and it was also fierce and fast.

However, its trajectory was simple and predictable, so always watch it carefully.

Then, he overlays the illusions of a huge black hand and a white hand on his left arm and attacks.

The black hand smashes people to pieces.

The white hand cuts them into pieces with its nails.

The black hand can be blocked and deflected, but the white hand cuts through weapons, so it must be avoided at all costs.

However, they did not notice the red glow in the vampire's eyes, nor did they see the invisible pattern rotating in the pupils.

Kwangyo Chilsal Ganggi. A magic technique that emits increasingly powerful energy with each kill, growing stronger with each life taken. It was not called one of the Ten Great Magic Techniques of the World for nothing.

Baekpal Sura Sword. A demonic technique that drenches the blood of the living, unleashing their primal instincts, shattering their sanity, and driving them into a bloodthirsty frenzy. This too was one of the Ten Great Demon Arts of the World.

The Wheel of the Demon. A vicious demonic technique that tears enemies apart with spinning blades, leaving them with irreparable wounds. This too (omitted)

Three-tenths of the Ten Great Demon Arts were contained in a single sword.

The six crescent blades, which had already been blocked before, collided with the massive sword, colliding again and again.

Sparks fly as the six crescent blades were cut in half.

And three heads, or more accurately, half of their skulls, fall to the ground with nothing left above their noses.

"How—?"

"I am Dook-ryun!"

A beastly cry.

The remaining four see the vampire swinging his sword at their slanted upper bodies, his arms pulled tightly behind him, and the white, massive palms overlapping them.

Ah.

The three slashed bodies spill onto the floor.

To be precise, they were two corpses with their upper bodies and waists severed, and a lucky survivor whose legs have been cut off.

"No! Kiyoooh!"

The lone general thrusts his crescent blade forward.

And then, kwaaang!

A purple lightning bolt flashes.

Kwaaang, kwaaang, kwaaang, purple lightning bolts flash repeatedly, and with each flash, the general takes a step back.

Kwaaang, kwaaang, kwaaang, kwaaang.

Eight flashes of lightning, seven steps backward.

The general kneels down with a thud.

"You are…"

The general regrets it deeply.

This creature was not a vampire.

How can a mere vampire be this strong?

I should have known its true identity sooner.

If only he had known its true identity…!

Then, with a thud, he buried his head and collapsed.

"You were a mere mortal…"

What a shocking revelation!

Unknown general, you were a mortal, an ordinary person, in other words, nothing more than a commoner!

What kind of nonsense was this?

Qing, who had been intoxicated by the rare slaughter, paused, and a faint blue light returned to his eyes.

It was that shocking.

What was this? Farewell, strongest? Commoner?

And the soldiers of Daewol were also shocked.

"A commoner, you were a commoner…!"

"Run! Everyone, run! The criminal! We must all escape!"

"Aah! We're all going to die! I heard the criminal's name! I heard the criminal's name! Dodokryeon was the criminal! The criminal's name was Dodokryeon!"

"No! Don't say that name! Aah! I can't hear anything!"

Even though they were enraged by the death of their comrade, the brave soldiers who had been charging forward suddenly turned and began to flee.

The criminal!

In the language of Daewol, it was "Pamyun"!

And Pamyun was the name of the most feared monster in the world of Daewol.

They were so terrified that they erased the name from this world and simply called him an ordinary person.

And if any of them were to return alive, the Great Moon Kingdom would remember the name of the demonic general.

The most feared demon, the return of the criminal.

However, even though they knew the Great Moon language, they had no idea about their culture, leaving the Qing people utterly baffled.

What on earth was going on?
