\chapter{Rice Blocks (3)}

Dong-joo's posture becomes slightly more respectful as he looked at the sword, which was now only half intact.

"Um, Great Hero. If I back down now…"

"Is that possible?"

Dong-joo's expression became pensive.

Only then does intense regret washed over him.

In Juanghu, he had been told repeatedly to be careful of children, women, and the elderly, but he had been so reckless and careless that he had not suspected anything.

It was his last chance.

\textit{I should have backed down when she said she'll let me go if I put away my sword. Is it Karma for swinging my sword in rage, when I supposed to protect Young Master?}

Dong-juk was filled with intense regret.

But that was only for a moment.

Qing pointed to Zheng Liuzhang with his hand.

"How can we save the remnant of the Blood Cult? It was planned from the beginning, so there's no need to look so remorseful. That guy over there was also my work, you know?"

"What?"

"It's also your end."

Qing raised his palm to eye level.

Three or four pearl-like lights appeared and slowly rotated on his palm, chasing each other.

Force Compression! Proof of Harmony Realm! That's so cool!

Of course, other than that, it has no practical use, and it's just a superficial display of power.

However, from the perspective of a Peak Realm martial artist, there was little that was more frightening than the Force Compression displayed by an enemy.

Dong-juk's eyes darted around.

He glanced over his shoulder once, then looked at Zheng Liuzhang where he was lying, making a soundless grunt.

The corners of Qing's mouth curled upward.

\textit{Is he trying to escape? Or is it just him? He can't carry his luggage by himself, can he?}

\textit{Is he trying to escape by himself?}

\textit{But it's ridiculous for a Peak Realm martial artist to try to escape from the clutches of a Harmony Realm master}

\textit{Even if it's just Peak Realm, he might have been able to attempt an escape, but with such a clear difference in skill, only someone at Transcendent Realm would dare to try.}

Qing quietly spoke.

"Of course, there is a way for you to live."

If you were going to die no matter what you do, might as well die in a cool way.

But that's not right.

Bad guys should remain bad guys.

Evil people should act evil.

They should kill without hesitation for small gains, be stingy in sharing what they get, and have no sense of loyalty, betraying others as easily as eating a meal.

"If you eat a fish you've caught, it will taste good right away. But if you learn how to fish, you'll be able to eat fish for the rest of your life. Oh, that's not right. Cancel. Again. Hmm. Hmm."

Qing waved her hand to retract her statement.

This was also a skill possessed by martial artists of Wulin.

So what if you're saying it wrong? What were they going to do if it's the wrong saying?

"If you eat a caught fish, it will taste good right away. However, you have to use it as bait to catch a big fish. You have to become that bait."

"What do you mean…"

"Kill the Blood Cult. Kill more of the Blood Cult. To do that, you need to know a lot about the Blood Cult, right?"

Fire blazed from the mask's eye holes.

It was a genuine killing intent, flashing red.

Dong-joo swallowed hard.

Seeing that terrible hatred, he could feel the gruesome state of Zheng Liuzhang with his whole body, and he understood where it came from.

"Just kill me."

"I won't kill you. I'll gouge out your eyes, pierce your ears, and cut out your tongue. Then I'll sever the nerves in your shoulders, and yes, now that I think of it, I'd better break all your fingers too."

Qing's eyes narrowed.

"Imagine it. You can't see or hear anything. You won't be able to scream or write to tell anyone. Every sensation you feel will be fear, and I don't know if the Blood Cult will let you live or kill you, but one thing is certain: you won't be able to beg for your life or even ask to die."

Contrary to her eyes, which were filled with fury, her voice was calm, as if she were stating the obvious, and her words rang clearly in Dong-chul's ears.

"Well, what are you going to do? Are you going to keep your word and end up like that, or are you going to live and make someone else to die in your place?"

At the same time, Qing's hand glow with a crimson light.

As if to say she won't let him stall any longer.

Dongjuk swallowed hard again.

Then, he glanced at the writhing Zheng Liuzhang who was crying with muffled sobs, looked back at Qing, and then back at Zheng Liuzhang again, where he saw the pitiful state of his long-serving superior, whom he had cherished like a brother or nephew.

Soon, Dong-chul's expression was filled with grim determination.

Then he opened his mouth with a fierce gaze.

"What are you curious about…?"

Inside the mask, Qing's mouth was torn from side to side.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In front of the acrid smoke rising from the mine, another black smoke rose, forming two lines.

The main building was on fire.

The large main building burned first, then the bodies of the Blood Cult members inside, and finally the wood from other buildings that had been torn down and piled up, causing the fire to rage.

Leaving the smoke rising into the sky behind them, a group of people escaped from the burning building.

They were the Blood Cult warriors.

The Blood Cult warriors moved south along the entrance road leading from the main gate and soon came face to face with a road stretching east to west.

Turning west, they saw a long mountain range rising up on both sides, blocking the horizon.

Following the road westward and climbing a little way up the mountain at its entrance, a steeply sloping hill finally appeared at the ridge.

The sight of the high hill was enough to take one's breath away. It was the Black Dragon Pass.

Normally, the warriors would have been complaining about the merciless slope, but now they just kept their mouths shut and climbed silently.

As the guards responsible for protecting the head of the family, how must they have felt, retreating after failing to protect anything and burning down the estate?

Therefore, with the gloomy expressions of defeated soldiers, the third-rate lower-ranked samurai were unable to even breathe heavily and were looking around nervously.

And the one leading the group, the Vice Captain of the Jeongga Guard, was about to reach the end of Black Dragon Pass.

In that moment, the view opened up, and the scene at the top of the pass came into view.

And what was the first thing he saw?

The Vice Captain's eyes widened.

\textit{What are those men doing? They are naked, not even men, but two creatures wearing only their underwear, crawling slowly on the ground.}

The Captain raised his hand to stop the group, drew his sword, and cautiously approached the unknown creatures.

The Vice Captain tried to be quiet, but the men crawling on the floor were so focused that they seemed unable to use their arms, crawling on their shoulders and legs.

\textit{They can't use their arms?}

"Y-young Master?"

The Vice Captain jumped out in surprise.

Then, the moment he grabbed the creatures's shoulder and flipped him over, a muffled scream erupts, filled with fear.

On both sides of his wide-open mouth, dried blood clots on his cheeks formed a single word.

On the right side, it says 'blood', and on the left side, it says 'calamity'.

Whether it means 'blood calamity'\footnote{Blood Cult literal name} or 'calamity blood,' the meaning was clear.

Then, suddenly, the Vice Captain's gaze turned to the remaining creature.

It was clearly the person who took his young master away.

"C-captain?"

The Vice Captain cautiously called out to his captain.

However, there was no answer.

It was the moment when the Vice Captain swallowed hard.

-Aaaah!!!

A scream erupted from the pass. And then.

-Kuhahahahaha!!! Blood Cult, die!

It was the voice of a woman, clear and beautiful, but it was accompanied by an incongruous, boisterous laugh.

The Vice Captain hurriedly got up and ran toward the pass, and saw his comrades being cut down without mercy.

Although her face was covered with a mask, she was clearly a woman, and her voice was that of a woman.

But more than that, a faint reddish glow emanated from the long, thick sword she held.

Sword Force, the mark of a Transcendent Realm master.

"I am the strongest bandit in the land! The legendary Tudulian, Um! The thief that steals the lives of you Blood Cult members! Hahahaha!"

The Sword Force fell.

The warrior raised his sword, but it was a meaningless gesture in the face of the Sword Force.

In that moment, the woman's blade bent at a right angle, then bent again at a right angle and fell.

The great sword that cut off the word's elbow by a finger's width rose again, cut off another finger's width, and fell again, cutting off another finger's width.

As the Qi left afterimages and drew countless vertical lines, the body, cut from the elbow to the wrist, rolled on the floor, and the forearm, which had lost its elbow, fell with the sword still in its hand.

The vertical lines gradually moved, and the Blood Cult warrior was literally cut into pieces. It was as if she was cutting food.

It was a terrifying sight.

"Krah! Another one down! I've stolen their worthless lives! This Tudulian! The strongest bandit, Tudulian! The legendary Tudulian!"

Although he had never heard of this alias or name before, it was clear that she had a great grudge against the Blood Cult.

After cutting dozens of his compatriots into pieces, Tudulian laughed maniacally, then quickly turned her head and swung her sword.

"Where are you running? Anyone who runs is rice! I'll mill you all!"

\textit{Mill!? Is that a word to use against people!?}

Before he can even process what was being said, there was a loud bang! Even from a considerable distance, the vibration can be felt through the soles of his feet, and with a loud cry, Tudulian moved so quickly that the Vice Captain loses sight of the enemy for a moment.

Then, she grabbed his comrade by the hair and…

\textit{Ugh!}

The Vice Captain swallowed hard.

Milling was the process of removing the husks from rice.

And that was literally what Tudulian had done.

When the movement arts, which had reached the level of a divine skill, trampled the rocky hillside, the sound of the ground shaking accompanied the figure of Tudulian as she leaped through the air.

The Vice Captain held his breath and carefully backed away.

He had never been so silent in his entire life.

Fortunately, the battle, or rather the massacre, was taking place on the hillside, so after a few steps, the horrific scene disappeared from view.

The Vice Captain repeated to himself.

\textit{This is not running away.}

\textit{I'm just saving the people who need to be saved first.}

\textit{They were just apprentice warriors of our Cult, so isn't it only natural to use their lives to save more precious ones?}

The Vice Captain, who had been backing away quietly, slowly took a deep breath.

Filling his lungs with air, he quickly grabbed Zheng Liuzhang and tucked him under his arm.

"Ugh!"

The Vice Captain felt as if his heart was falling to the ground at the sound of Zheng Liu's scream.

But he couldn't waste anymore time.

The Vice Captain rushed forward and grabbed Captain Dong-joo's body with his left arm.

"Huh!"

The screams on both sides were bloodcurdling.

Before he knew it, sweat was pouring down his back, making him feel cold.

With a cripple tucked under each arm, the Vice Captain kept running.

Towards the hill below, leaving behind the screams of his dying subordinates.
