\chapter{Rice Blocks (7)}

Qing was frowning at the slightly stale taste of rice balls..

"What, it went bad in just one day…"

It wasn't unusual.

The hot, humid weather was the perfect environment for food to spoil quickly.

Besides, rice balls in Zhongyuan tended to go bad easily.

Sticky rice tended to go bad quickly when left out, and the ingredients inside weren't fresh to begin with.

There were no refrigerators in Zhongyuan, so the rice had to be stored at room temperature throughout the entire production, distribution, and sales process.

The rice balls smelled musty, and Qing ate them with her eyebrows furrowed, chewing slowly.

\textit{Doesn't mean I 'll throw them away. They are still edible. There is no mold or rot, just a little moisture.}

\textit{I used to eat worse things than this.}

\textit{Still, after eating only expensive foods for the past few years, I guess I can't help but be picky.}

That's when it happened.

A foul odor hit Qing's nose.

Something sour and unpleasant, like the smell of rotten food, or the stench of shoes that have been soaked in rain and not dried properly—

But amidst that foul odor, there was a subtle, refreshing scent that was almost intoxicating.

Qing's eyes lit up.

\textit{Is that alcohol? The smell of alcohol?}

Qing loved alcohol. She could drink a whole jar of it and never get drunk, but she loved it nonetheless.

Some might say that only a dog could smell alcohol amid such a foul stench, but in fact, it was a very familiar combination to Qing.

\textit{Hmm, it smells like a beggar drinking alcohol.}

It was a combination she had always smelled while living as a beggar in Jianping, and suddenly, memories of that time came flooding back…

It was a time when she really wanted to have a drink, because it was hard to stay sober.

She didn't know where those beggars got their alcohol, but they drank it often, sometimes even frequently.

If she tried to talk to them, they would hit her, so she couldn't talk to them, and if she got close to them, they would hit her, so she couldn't get close to them, so she just stood far away and drooled.

If she caught their eye, they'd beat her up for ruining their buzz, saying she were like plague-ridden ghosts.

\textit{Damn bastards, I hope they end up in hell.}

One day, a drunk beggar who was in a good mood offered her some leftover alcohol, but instead of giving it to her, he poured it on the ground right in front of her.

So she quickly gathered the dirt, squeezed it out, and drank it. 

\textit{Even though it was cheap, low-quality alcohol, I still can't forget that taste…}

\textit{It must have been entertaining to watch me squeeze the alcohol out of the dirt and drink it, because when I was enjoying it, they would peek over and let me drink it. Hmm. What bastards.}

Qing scattered away the dirty memories.

\textit{Anyway, there's no way there would be beggars in the mountains out of the blue, so they must have been mountain men such as herb gatherers, hunters, or honey gatherers who came out for a hike.}

\textit{It's been more than a day since I entered the mountains, and it's about time to reach the city.}

\textit{In this world, it was not uncommon for mountain dwellers to set up temporary shelters in the shallow mountains and go on mountain hikes for a few days.}

\textit{Surely, they are melting the hardships of their labor with alcohol, giving off the smell of hard work…}

\textit{What's more, this is perfect timing.}

\textit{I plan to monitor the movements of Five Poisons Sect in Jinping County, and once I get to know the mountain dwellers in the city, I can naturally blend in as an herbalist from out of town who has come to gather herbs.}

Qing rustled her clothes, deliberately making noise as she moved forward.

It was only polite to make some noise when approaching someone.

Since she had to pretend to be an herb collector, she picked some herbs that catch her eye and puts them aside. 

\textit{I can share some with others and drink together. Yes, perfect.}

Qing swallows hard and pushes through the bushes.

And finally, there they are.

She saw the mountain dwellers… or rather, what?

Their clothes were covered in dirt and damp, but they look like they were dressed in martial arts uniforms.

\textit{What is this? Why there're martial artists in the mountains?}

Whether it was because they looked shabby or because they had committed a hundred evil deeds, they looked exactly like members of the evil sect.

Of course, even if they were disqualified as humans due to their evil deeds, they weren't exactly suspicious or anything, as they were just average members of the evil sect.

"Who are you?"

"Um, my child is sick, and I heard that the herbs from Dzahai Mountain Are very effective…"

Qing decided to pretended to be an herb collector.

With the entrance to Jinping County just ahead, there was no point in causing a commotion.

However, when encountering such people, it was rare for things to go smoothly.

It was rare, but it did happen.

\textit{Yes, I wonder how the man who 'saved' me in Mount Lao is doing. He was a human being, unlike most evil people.}

In any case, Qing pretended to be cowering.

The warrior glanced at Qing and said,

"What are you? A mountain woman? Hmm, I see. But you really have no fear, daring to come to Dazhai Mountain to gather herbs."

"Yes, sir?"

"Dazhai Mountain is the territory of our Five Poisons Sect. And here you are, a thief who dared to steal herbs from the mountains of the Five Poisons Sect?"

Qing froze.

\textit{What did he just say? Our Five Poisons Sect?}

\textit{Why is the Five Poisons Sect here?}

\textit{Five Poisons Sect was said to occupy the best location in Jinping County, so why are they drinking alcohol in this mountainous area, stinking of rot?}

To Qing, who was unaware of Five Poisons Sect's ten-sided ambush strategy, it was like encountering a complete stranger.

"Priest\footnote{position in Ten-Sided Ambush, maybe}, stop talking nonsense and follow the rules. Listen, you climbed Mount Dazhai without the permission of the Five Poisons Sect. You must have known that if you were caught, you would be killed. You dared to covet the property of the main branch. You will pay for your crime with your life."

What is this nonsense?

You're going to execute me just because I picked some herbs in the mountains?

\textit{No, is that some kind blood oath?}

\textit{Hunting ground control? Death for disobeying?}

Suddenly, a scene flashes through Qing's mind.

When she saw Lan-Ah searching for Zheng Mansion's medicine documents, she was sure she heard something about the Five Poisons Sect and some kind of forest treasure.

If the black market dealer was selling it secretly, that meant the Five Poisons Sect was properly controlling it.

\textit{Still, that's not right. Killing someone for picking some herbs? That's crossing the line.}

\textit{What kind of people are these?}

Qing gripped the handle of the moonlight sword disguised as a cane.

That was the moment.

"Executioner\footnote{position in Ten-Sided Ambush, maybe}, wait a moment. The child is sick, isn't he?"

\textit{Oh? Another display of humanity?}

\textit{Even one of the two with greater evil deeds shows unexpected humanity?}

Qing temporarily suspended the sentence.

"Even if her situation is dire, we cannot break the rules of the sect for such a trivial reason. If we let her go now because she was pitiful, then later all sorts of people will come with all sorts of excuses and steal the sect's property. Therefore, the rules must be strict, and there can be no exceptions."

"That's not it. Didn't Executioner starve for quite some time? Her child is sick, and the circumstances are dire. If she pays with her body, you'll have some fun and accumulate merit—isn't that a good deal?"

"Hm."

"Looking at her hands, she seems quite young, doesn't she? You enjoy her first and leave her clean for me. Okay?"

"No, that's not right. Let's enjoy her later. When we go down later, I'll give her a good beating at Gwangnaru. No matter what, we can't break the rules of the sect."

\textit{Hmm. That's right, as I thought.}

\textit{They seem to be brothers, but as expected of brothers, they are very similar.}

\textit{One wants to kill someone for picking herbs in the mountains.}

\textit{The other is a pervert who says he will spare my life if I lets him have his way.}

\textit{It is difficult to say which one is worse. It is truly a mystery.}

Qing was so stunned that she forgot she was pretending to be a herb collector and just watched the scene. Then, the man called Executioner slipped his hand into his sleeve and—

Sshh!

A dagger flew toward her neck!

However, to Hwa-gyeong, a master swordsman, it seemed slow.

Even the thrown dagger was slow.

"Guh!"

Qing grabbed her neck and collapsed to the ground.

To be precise, she grabbed the dagger between her fingers and pretended to be hit in the neck before collapsing.

After that, she suddenly feels at a loss.

\textit{Hmm, what happens to someone who gets stabbed in the neck?}

\textit{Should I shake this body violently?}

\textit{There shouldn't be any blood gushing out before he pulled out the sword, so I'm not dead yet, right?}

Qing didn't want to cause a commotion.

Qing's goal was to scout the Blood Sect, so she didn't want to stir up trouble.

Unless the results of her reconnaissance were very promising.

In any case, she had no intention of acting recklessly on her own like in Mount Lao and running away if things didn't work out.

\textit{This is a matter related to the Blood Sect, so if I rush in and something goes wrong, it won't be just my problem.}

\textit{For now, I've already started, so I might as well continue.}

\textit{I'll grab one of them and find out why they're in this miserable place when they have such a nice home.}

\textit{And I'll find out what the Blood Sect is up to…}

Qing lay on the floor, trembling.

Gasp, cough. She was gasping for air.

\textit{Bido isn't a disposable item, so if I wait, they'll come to retrieve it.}

\textit{I'll finish one off with a single blow and subdue the other.}

\textit{Hmm. If possible, I'd prefer the executioner to come.}

\textit{In my experience, people who strictly follow the rules of their sect are also deeply devoted to it.}

\textit{It's a prejudice, but I think the Priest would be more likely to talk.}

But then, what about the mess?

"Cough. Senior. Then I'll go and dispose of the body. If it rots nearby, how will we deal with the smell?"

"Why are you volunteering? No, you, don't tell me you're going to touch the corpse…"

"Come on, Senior. If we finish before it's time, it'll be the same. Let's just get it over with and bury it quickly."

"… Sigh. Don't be gone too long."

\textit{What's there to finish? Ah.}

Qing was horrified.

\textit{Is this some kind of perversion? There really are some disgusting people in this world.}

Qing lay down and estimated the distance.

Four steps, three steps, two steps.

And now!

Qing jumped up and lunged forward.

The Moonlight Sword shot up toward the sky.

The blade wrapped in the torn cloth shot up into the man's groin, immediately cutting through the cloth and slicing through flesh and bone before flying into the sky.

The eyes of the remaining members of the Five Poison Sect's Executioner widened as if they were about to burst.

The starlight flickered, and the dead priest's split body fell to the left and right.

Was it a dream or reality? For a moment, he was stunned by the unbelievable scene.

Bang! Something suddenly fell down with a rumbling sound from the soles of his feet, and his breath was cut off.

It was sheer panic, the moment when his mind went completely blank.

"Hey, you dropped your sword. Here, I returned it to you. Shouldn't you be grateful?"

A burning pain like fire pushed against his shoulder, as if to laugh at him, asking why he was losing his mind.

The Five Poisons Sect's member's right arm went limp.

The sword he had thrown slowly dug into his bone, severing his nerves.

"Ugh."

"What kind of treasure did you bury in the mountains that you would try to kill a poor woman who was just trying to gather herbs to treat her sick child? Even those bandits would ask for money first before drawing their swords. You guys are worse than common bandits!"

"Ugh…"

"I, the supreme bandit, who eats rice at home, the tasteful Xiatian, ah, that's wrong, I, Tudulian, will not forgive you!"

Xiatian was wrong, but whether she said Xiatian or Dulian, it was all the same.

It was impossible to tell the difference even for those listening, and the eyes of the Five Poisons Sect followers widened when they heard the name Tudulian.

"But I, Tudulian, am not like you bastards who kill people indiscriminately without asking any questions."

It was an absurds words for for The Five Poisons Sect followers who had been cut in half.

But the dead cannot hear.

"If you answer my questions obediently, there will be no more bloodshed. Do you understand? Don't shout or you'll end up with a hole in your neck. Now, take a deep breath."

Qing growled and loosened her grip on the man's neck slightly.

"Huh, ugh, ugh, ugh."

Only then did Five Poisons Sect, whose throat had been squeezed shut, breathed in roughly.

Then, with eyes filled with hatred, he squeezed out the words,

"You, Heavenly Blossom Sword, even if I chew you up, it won't be enough."

Qing hurriedly choked him again.

At the same time, her large eyes darted around, as she couldn't hide her bewildered expression.

\textit{What? Heavenly Flower Sword? How did he know?}
