\chapter{Rice Blocks (11)}

No matter how much he enjoyed killing, now he felt nothing but disgust.

If he had simply enjoyed cutting flesh and bones, he wouldn't have had to kill living people.

He could have cut up corpses, or even opened a butcher shop, and every day would have been ecstatic.

However, the act of cutting human skin, tearing muscles, and breaking bones was just a process.

What Cheonsalsung truly sought was grief, sorrow, and pain, and the agonizing emotions created by a series of dismemberment were the purpose of slaughter that brought him pleasure.

In that sense, killing the Oedokmun followers was not slaughter at all.

Those who were prepared to die from the beginning, those who knew they would die, were no different from living corpses.

Of course, there were also real living corpses.

"Kyaaaah!"

In the dark forest, monsters with bloodshot eyes rushed forward.

With their naked bodies and twisted limbs, they crawled and jumped, their red eyes drawing tails and approaching in complex shapes.

A weak-minded person would have fainted, thinking that monsters had appeared, or shouted in horror, wondering what kind of sorcery this was.

Instead, Qing just frowned.

Since Five Poisons Sect has joined forces with the Blood Sect, it was only natural that monsters from the Blood Sect would appear.

In fact, it would have been suspicious if they hadn't appeared.

Now we can be absolutely certain that the Blood Sect was involved with Five Poisons Sect.

And those guys didn't seem to get along with me. They were spreading malicious rumors about me, saying I smelled bad…

Suddenly, the monster in the lead leaps into the air.

As if it were a dolphin, it twisted its body and slowly rotated, then raised its bent arms and drew a diagonal line.

Kang! The blue armor blocked the monster's claws.

I don't think it's the same monster that was in Hangzhou.

It seems there were different types of monsters.

However, it was the most hideous of all the monsters of the Blood Sect I had seen so far.

Should I call it leprosy or leprosy? Its face was half melted and rotten, and instead of sweat, green pus flowed down its entire body.

Damn it, at least put some underwear on it. What kind of visual attack was this?

This was definitely a monster related to poison, right?

That was the moment.

The monster jumped away on all fours, its lips quivering.

Gasp, no way?!

Qing's expression turned pale as he split into eight.

Then, with a squeak, a powerful jet of green fluid shoots out.

No, they're spitting!

They're not some kind of alien monsters!

However, Qing quickly steps forward and stomps on the monster in front of him, revealing his true form in the middle of the monsters.

"Kieeeek!" "Kieek!" "Kiheeeek!"

The monsters, their bodies torn apart, leap into the air all at once!

However, Qing's toes were already high above his head, and his left foot, surrounded by a whirlwind of black debris, quickly slams into the ground.

Kwaang! As the ground caved in, the monsters rushing from the air were crushed by the powerful pressure and slammed into the ground at once.

Heavenly Demon Reigning Steps, Je Pal Bo. Manin Angbok.

All shall bow their heads to Cheonma.

It was a terrifying technique of the Heavenly Horse-Kicking, completely defying the laws of physics, as it slammed into the ground but instead of bouncing back up, it was crushed by downward pressure.

Of course, with the cosmic mysteries of Zhongyuan, anything was possible when ki was at work.

Qing's Cheonma Shin-gong was still incomplete, and his own level was insignificant compared to Cheonma, so Cheonma-bal-gurigi was only enough to stop the enemy once.

The monsters that were crushed like frogs rise up again at once.

However, Qing jumps one step ahead, flips his body in midair, and shoots off into the sky.

Yoo Seong-rak's shooting star fall.

The tip of the Moonlight Sword pierces the monster's back, skewering its heart, and the remaining force digs into the muddy ground.

And then, at that moment.

The monster's decaying body swells up like thick liquid boiling over.

Oh no. Could it be? Is it self-destructing?

Qing hurriedly draws his sword.

With a strange, sticky explosion, something hot and sticky splatters all over his body.

At the same time, a pungent smell hits his nose.

"Kieek!!" "Kieek!!!"

"Damn, what a dirty fight!"

Qing pushes off the ground and charges forward.

You Five Poisons Sect bastards, what kind of dirty fight was this?

"There!"

Pibik, piiik—!!

In addition to the monster, there were Five Poisons Sect warriors.

The tropical rainforest was already blocked by trees, bushes, and branches.

Hiding behind, they throw daggers, blow them with their mouths, detonate dagger containers, and when they seem to fall awkwardly, they release sticky poison bags that emit a pungent odor.

And occasionally, they throw spears.

Kang!

Qing's gaze as he deflects the spear was unusual.

His pupils have shrunk to the size of beans, and the whites of his eyes, which have become more prominent, were flickering.

"There, there…!"

I was going to give them a fair fight.

These guys were crossing the line…

Qing stomps on the ground.

The Moonlight Sword was already emitting a fiery red energy that was visible to the naked eye.

The Moonlight Sword cuts through the air horizontally.

The sword's energy cuts through everything in its path, causing the giant trees to shake violently.

The trees in the tropical forest, already tangled together, do not fall immediately when cut.

However, the upper bodies of the Odokmon monks hiding behind them fall down with a thud, their eyes wide with disbelief.

The Odokmon monks struggle, but finally manage to grab their sleeves.

Ah, not again!

Qing immediately changes direction.

With a loud bang, smoke billows behind Qing, accompanied by the tiresome sound of gunpowder exploding.

Kieeeek!

And through the smoke rush naked, blood-covered monsters from the Blood Sect.

However, a flash of sword light appears.

It was clearly a single sword, but with a single swing, three streams of energy shoot out.

It was the image of the 108-bladed sword, modeled after the claws of a beast.

The monster, cut into pieces, rolls on the ground, simultaneously bumping and jolting.

As Qing stomps on the ground again, there was a loud crack!

Suddenly, the ground where he stepped on sinks.

He stepped hard, so his thighs sink quickly, and at the same time, he feels a sharp pain in the front and back.

It was a simple trap using the principle of a lever.

When stepped on, the boards beneath the trap rotated, striking with nails coated in poison.

Of course, the nails couldn't pierce Qing's muscles, especially the thighs, where the strongest muscles in the body were located.

However, they could pierce the skin slightly.

When pressed with a finger, blood would seep out, revealing the true nature of the sting.

"There was a trap!"

Qing shouted angrily.

These despicable creatures, calling themselves martial artists, how dare they use traps…!

The trap I set up in Zhangjiajie wasn't really a trap, but humans were creatures that only feel pain and injustice when they were hurt.

Qing was truly human, or rather, he had a very human side.

However, the color that flowed from his eyes, a color that existed in all colors but was unlike any other color in the world, was not very human.

Kieek!

A blood cult monster rushes toward you on all fours.

Then, with a snap, Qing's head turns at an unnatural angle.

To exaggerate a little, it's almost as if he turned around completely.

His eyes, filled with malice, meet the monster's milky, rotten eyes.

Kieek!

The Blood Sect monster let out a fierce cry and quickly backed away, crawling backward in reverse of the way it had charged forward.

It was an impressive scene, as if time had been reversed, which was one of Qing's specialties.

However, that moment was short-lived. Deeng…!!!

Woo-woo-woo… A huge echo shook the entire area. A faint, eerie halo shines behind Qing's head.

It was the Imagery of the Tathagata, containing the mercy of the Buddha, but the head behind the halo was so hideous that it does not fit at all.

That was the moment.

Whack!!! The spear rips through the air and rushes towards Cheong's head.

And bang!

The blue figure's head jerks to the side, and the spear spins wildly and flies away.

In that instant, something clicks inside the blue figure's head.

With his head still bent, the blue figure moves only his fierce eyes toward the direction from which the spear came.

Following that, his face, covered in mud, blood, and poison, contrasts with his dazzling white teeth, which form a crescent shape.

"Huh."

Elder Five Poisons Sect, who threw the spear, unconsciously exhales.

Then he immediately turns around.

No, what kind of monster have the Zhengpa created? How could the Zhengpa create a monster more terrifying than those of the Blood Cult?

What kind of female warrior was this Zhengpa? Is there really such a demon in the world?

The killing intent emanating from her was so intense that just looking at her makes my legs tremble and my heart sink.

It makes me wonder if the so-called "thousand-year-old killer" really looks like that.

Actually, since it was the thousand-year-old killer himself who was hit, one could say that the insight of a long-lived warrior was worth the price of a long life.

The elder hurriedly puts the flute to his mouth.

Piiii, piiii, piiii!

The flute sounds different from before, with a longer breath.

Usually, such clear flute signals were used to convey the most important information.

Usually, it means retreat.

However, although the elder's expression was grim, he does not look frightened or discouraged.

If so, it could be a signal for a change in strategy.

For example, a change in tactics.

-Piiii, piiii.

The expression on the face of General Five Poisons Sect, who was coordinating the situation with flute signals from the center of the formation, becomes cloudy.

It was a sign that the worst has happened, that the enemy's forces were stronger than expected and the ambush may be broken.

It was a signal he had not expected at all.

However, the situation was not going well.

The original plan was to threaten them with hidden weapons and poison, driving them like animals and causing them pain.

The idea was to make the fleeing beasts suffer as much as possible, slowly and gradually poisoning them until they lost all hope and screamed in despair.

And finally, they would be driven into the center of the formation.

At that moment, they would arrive before Five Poisons Sect, drink the blood of their enemies, and hold a memorial service to comfort the souls of his disciples.

However, the plan was flawed from the beginning.

Instead of being chased and driven away, wouldn't the Heavenly Sword be hunting his disciples as if he were the hunter?

The original training was to form a net of fire within the formation through organic movements and gradually drive them deeper into the formation.

But the plan can be revised.

If the chase doesn't work, use a decoy.

We'll just switch from hunting to fishing.

So, the general was busy coordinating complex maneuvers, listening for the flute signal to keep track of the enemy's location, and sending signals to his disciples to draw the enemy's attention and lead them as close to the center of the formation as possible.

And then, an emergency signal?

As we had assumed in the worst-case scenario, the enemy faction did not come in large numbers, but only one, a young girl who had not even tasted blood.

And yet, the ambush was in danger of being broken?

But this emergency signal can only be given by the elders.

An elder would not have made such a rash decision.

And if we've assumed the worst-case scenario, we should have prepared accordingly.

With that, the commander picks up the fireworks from the tactical table.

Ten-sided ambush formation, as my countermeasure.
