\chapter{Rice Blocks (1)}

Even as the interior continued to collapse, the mine emitted thick smoke.

Fortunately, the fallen soldiers were not seriously injured and regained consciousness shortly after.

They complained of dizziness and nausea.

"First, close the mine. This is coal for our people. We can't let it all burn."

Thus, the work to close the mine resumed.

Progress was slow as they were careful because of the poisonous smoke, but as long as they remained cautious, there were no further signs of poisoning.

Of course, it was only because the poison powder that Tang Lan-Ah had set up had worn off, but the guards were so naive that they couldn't even imagine that someone had attacked the mine.

While the captain of the guards was successfully blocking the mine entrance, his subordinate returned from searching the miners' quarters.

"Captain, the dormitory is empty."

"What?"

"They probably went in to put out the fire…"

The subordinate trailed off.

The captain let out a sad sigh.

\textit{The smoke alone was enough to make the guards foamed at the mouth, so how could the miners, who knew nothing of martial arts, have survived?}

\textit{The fire started in the internal reading room, and all the miners rushed to put it out without thinking about saving themselves, but they all met a tragic end.}

If Qing had heard this, she would have laughed.

Was he naive, or did he have such a high opinion of the group?

Wouldn't it be normal to think that someone attacked them, killed them all, and set fire to the coal mine?

However, this was the evil of a brainwashed society.

When people were constantly indoctrinated with propaganda that all compatriots must strive for the liberation of all compatriots, and that they were already striving for it, it becomes common sense.

However, the illusion did not last long.

When the Blood Cult warriors returned to the mining village at sunset after completing their arduous work, they were greeted by an eerily quiet silence.

Corpses were visible through the wide-open gates.

Only then did the captain of the guard realize the reality of the situation.

At the same time, the hairs on his body stood on end.

\textit{It was an ambush!}

The enemies had killed his fellow miners and set fire to the mine, then took advantage of the chaos to attack the mansion.

Then, a thought struck him!

"No! Young Master! Young Master! Are you there? It's Dong-Juk! Young Master!"

The captain of the guards and Dong-joo rushed inside with heavy footsteps.

The soldiers hurriedly followed behind them.

"Young Master!"

Despite his desperate calls, there was no answer.

Dong-joo rushed into the Master's office.

Looking around frantically, Dong-joo saw a familiar body dressed in silk lying in the corner.

For some reason, his face was covered by a cushion, so Dong-joo couldn't be sure if it was him, but it was his favorite clothes.

Dong-joo's heart sank.

However,

Looking closer, he saw that the chest of the body sticking out from under the cushion was very carefully covered, but it seemed as if parts of the body were missing.

"Young Master? Young Master, it's Dong-joo!"

"…"

"Young Master?"

\textit{Was he in a deep sleep?}

Dong-joo quietly approached and carefully reached out his hand to touch the body, but at that moment…

"Huaaaah! Ugh! Ugh! Aaah!"

A bloodcurdling scream erupted.

Not only was the volume of the scream terrifying, but the pronunciation was completely garbled, like the cry of a mute person.

"Young Master?"

"Aah! Aaah!! Ugh! Uh, aah!!"

"Calm down, it's Dong-joo, Young Master, it's me, Dong-joo."

Dong-joo's words were cut off.

Under the cushion that had been knocked aside by his unnatural movements, Zheng Liuzhang was revealed in all its gruesome glory.

His eyes were horribly swollen, blood stains were smeared around his mouth, and dried blood crusts were caked on his earlobes.

\textit{Who, how, and why did someone do such a brutal thing…!}

Dongjuk frantically examined the body of Zheng Liuzhang and tried to realign the dislocated shoulder.

"Aaah!"

"Young Master, it's me. Calm down, calm down."

Dong-jook hugged Zheng Liuzhang tightly.

His body shook with fear.

Even though his shoulders were now aligned, the pain had only subsided, and he tried desperately to break free with his limp arms, which had torn all the ligaments.

To the invisible and inaudible bus stop, the current stimulation was pure terror.

This went on for a while.

Suddenly, Zheng Liu's convulsions ceased.

It seems to have confirmed its safety.

"I'll take you to a safe place first."

"Ugh."

"Young Master, it's me. Stay still, you can't hear anything. Excuse me."

Dong-juk carried Zheng Liuzhang and left the office.

"Captain?"

"I'll take Young Master with me first. You gather the guards, dispose of the bodies, and follow us after burning them with the estate."

"You mean to Five Poisons Sect."

"Yes. Time is of the essence, so I'll go first. I leave the rest to you."

"Ugh!"

"Shh, Young Master, it's okay, it's okay."

Dong-juk immediately steps on the jingak.

His footwork was neat and precise, and his martial arts skills were quite remarkable.

In an instant, Dong-juk escaped from the main gate of the manor and ran down the road with all his might…

Someone rushed out from the main gate.

And far away, at the foot of a mountain.

Among the fields of Zhongyuan, a figure watched from a spot in the woods on a forest slope, their large eyes shining from behind their mask.

It was as if they were trying to figure out who the figure in the distance is.

Then, the corner of the masked person's mouth curled up crookedly.

And then.

With a small noise of the bushes rustling, the masked person disappeared without a trace.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was a small ridge between Zheng Mansion and Gejiu, and the people of this village called the road that crossed it Black Dragon Pass.

It may seem like a grand name, but in fact, there were over a hundred passes with the name Black Dragon Pass in Zhongyuan.

It was a name commonly given to passes that were blocked by thin, long mountain ridges and were quite steep and difficult to cross.

The long, narrow mountain range resembled a dragon, and among dragons, the black dragon was synonymous with a vicious dragon in Zhongyuan, so it was a perfect name for a difficult pass.

Therefore, even without actually experiencing it, one could imagine that Black Dragon Pass was a steep and dangerous pass that would make one cry out in pain.

And there was one person, no, two people, no, was it just one person?

\textit{If someone was carrying another person while running, should it be considered one person running or two people running?}

\textit{It was one person running, but two people moving, hmm, I had never imagined such a thing before.}

Qing briefly lose focus, then noticed another runner breaking through the middle, and quietly moved about thirty steps inward toward the highest peak.

Then, standing in the middle of the path, she drew a large, ambiguous sword—too big to be called a sword and too small to be called a greatsword—and held it like a staff, leaning against it.

It was in a position that could not be seen from below the pass, but immediately visible as soon as you finished climbing the uphill road and reached the top of the pass.

And how much time had passed?

Finally, the Blood Cult warrior who had been carrying Zheng Liuzhang finished climbing the hill and jumped up.

Qing took a deep breath and muttered in low voice.

"Stop!"

Qing couldn't understand how it was possible, but as a martial artist, she knew that one could amplify one's voice with inner arts.

If Qing had been a science major, she might have wondered what kind of influence the mysterious cosmic element called Qi might have on the vibration and amplitude of sound and the medium of air.

Unfortunately, Qing was a liberal arts major, so she didn't have the advanced way of thinking to wonder about the principles behind phenomena that simply worked.

Anyway.

The Blood Cult warrior, Dong-juk, couldn't stop himself and jumped back, creating some distance between them.

Holding onto Zheng Liuzhang with one hand, he leaned forward as if to hide him and drew his sword with his other hand, aiming it at Qing.

Then, with a fierce expression, he looked at the masked person blocking his way.

"…Who are you?"

The large eyes revealed by the mask's eye holes drew a beautiful curve.

"If you ask who I am, it is only natural that I should answer! I am a bandit!"

"What…?"

"People throughout the land call this woman 'The Strongest Bandit' and fear her. Or rather, they were afraid to even utter her alias, calling her 'the rice eater'.

"The Strongest Bandit…?"

It was not unusual for bandits to give themselves grandiose aliases.

Rather than saying, 'I am Bandit So-and-so', it was more effective to give yourself an evil-sounding alias such as 'Assassin' or 'Killer'.

But the strongest bandit?

When bragging was taken too far, it just looked ridiculous.

And what does 'rice eater' mean?

Does that mean there were people who don't eat rice?

While Dongjuk was lost in confusion and momentarily forgot the urgent situation, Qing straightened her chest and shouted.

"Yes! I am the strongest bandit, my name is, um, name."

Qing thought for a moment, then said.

"Yes, this woman is the strongest bandit, Elder Tudulian!"

The strongest bandit, Tudulian! A rice eater!

Then Qing pointed his sword at him and said,

"Anyway, this is a robbery! Give me everything you have!"

Dong-jook narrowed his eyes.

He could easily cut down a clumsy bandit with a single sword stroke.

But it was difficult to deal with someone who openly used a fake name.

Moreover, he had to protect his young master, Zheng Luzhang, who was in a situation where he couldn't even recognize any danger, let alone protect himself.

Dong-jook stabbed his sword to the ground in front of him.

This was a common technique used when a sword master could not sheathe his sword and had no free hands.

Then, he reached behind his waist, unfastened his money pouch, and threw it forward.

The money pouch flew in a parabolic arc and landed precisely at Qing's feet.

Qing laughed shamelessly, picked up the money pouch, and looked inside.

Then.

"What the hell? Just coins? Are you a beggar? A beggar? You have no money?"

"…You got the money, now scram."

"No, this way I can't do business. Look, I've been standing here all day. How many customers do you think come here in a day? None. There were none. Even so, I stayed here even though it rained, snowed, and stormed. I worked so hard, and now a customer who came after such a long time throws me just a few coins. This isn't right. What was my effort for?"

Qing was fully immersed in her role as the strongest bandit, Tudulian.

If Tian Youxue had heard this, he would have laughed, saying that this woman was born to be a bandit.

As usual, Dong-juk rolled his eyes from side to side at the nonsense bandits were spouting.

Bandits never worked alone; they usually ambushed their victims from both sides, with one of them starting a fight.

"Hey there. I can see you eyes darting around. Listen, sir, let's settle this nicely. You're being insincere. Why don't you just leave? Oh, wait, the clothes you're wearing look quite expensive. Wow, the clothes your son wearing look like silk! They're stunning."

"Watch your mouth—"

"Hey, have I seen a guy a or two with a sword before? Look at this. This is Sword Thread. Only a master can do this. Hey, I'm confident in my skills, so I'm not just showing off. Don't you understand the situation?"

Dong-joo froze. The Qi was already clearly visible, and a thread-like sword beam seemed to bloom around it.

It was proof of a martial artist at Peak Realm.

Dong-joo's eyes were filled with suspicion.

\textit{When the mansion was attacked, even if it was in the countryside, there is a Peak Realm martial artist robbing people on a nearby mountain pass? Could it be…}

"You two are both rich and handsome, wearing nice clothes. I'll let you keep your underwears. It's not like it matters if a man takes his clothes off. Hehe, it's been a while since I had a treat for my eyes."

Dong-joo dismissed the thought.

Regardless of the attack, this woman was very rude, and her vulgar behavior made Dong-Jook certain that she was a thief from birth.

Dong-Jook was conflicted.

Should he took off his clothes?

However, unlike her vulgarity, the enemy in front of him was a genuine Peak Realm martial artist, and she was likely quite skilled. In the worst case, she could be at the same level as Dong-Jook.

Furthermore, it was rare for a bandit of this caliber to travel alone, so there might be accomplices lying in wait nearby.

Dong-jook gritted his teeth.

"You said you are the strongest bandit, Tudulian. Do you think you'll get away with this? Don't you know who I am? Aren't you afraid of the consequences?"

"Oh, how scary. Have many times have I heard that? Anyway, I was planning to close up shop and leave because the business here is so bad, so I'm glad I got one last customer. I'm going broke, but there's no customer. They say that half of this business is financed by the customers."

Qing laughed unpleasantly.

"What's the big deal with aftermath? What can customers do if you close up shop and leave? So just take your clothes off and go. You think you're something special. Tsk, tsk."

The veins on Dong-joo's forehead bulged.

This was the intangible poison, the tongue that turned people's clothes inside out, the mouth of fear.

The moment you mix words with it, you're already addicted!

Qing grinned.

\textit{What's wrong? If you're angry, come at me, then.}

\vfill

\begin{lstlisting}
	Korean meme, referring to the practice of farming MMMORPG's in-game items to resell
\end{lstlisting}