\chapter{Rice Blocks (6)}

If you follow the road southeast from Gejiu, you will arrive at Hekou, a city surrounded by high mountains on both sides.

Hekou was a border city divided into two halves, with the northern part belonging to Zhongyuan and the southern part belonging to Dayueguo\footnote{大越國; Dai Viet Kingdom}.

In this era, borders were usually formed by rugged mountain ranges or large rivers that were difficult for people to cross, so it was natural that high mountains stretched out to the left and right.

Among them, the high mountain blocking the west was Dazhai Mountain.

It was also a mountain that Qing had to cross.

If you draw a straight line westward from Honggang at the entrance to Hekou County, you will find Jinping County, where Five Poisons Sect was located in a basin surrounded by Dazhai Mountain.

However, Dazhai Mountain was quite notorious in southern Yunnan Province.

This was not only because of its rugged terrain, but also because a dense tropical rainforest spreads out to the south from here.

In fact, martial artists in Zhongyuan tend to look down on the rainforest.

There were many rugged mountain ranges in Zhongyuan, but we martial artists have overcome even those sheer cliffs.

But a jungle?

What could be dangerous about a mere forest?

Furthermore, people from Qing's homeland tend to take mountains lightly.

This was because the mountains in Qing's homeland were low and gentle, so there were few incidents of people getting into trouble.

In short, since there were no truly dangerous mountains in the country, mountains were considered a spiritual home and even the best place to build camaraderie at work.

And Qing belonged to both groups.

As a master of transcendent martial arts with a body immune to all poisons, what danger could a mere tropical rainforest pose?

And so, Qing set foot in Dazhai Mountain.

Today's topic was the women who came out to gather medicinal herbs.

She was dressed in shabby clothes and carries a basket on her back.

If she ran into someone, they might tell the Blood Cult.

Even if that doesn't happen, when she arrives in Jinping County, it would be suspicious if a martial artist came down from the mountains where there were no roads.

However, herbalists were everywhere.

She was worried that her identity would be revealed, but she didn't think for a moment that the tropical forest was dangerous.

Of course, would that really be the case?

The tropical forest was no joke!

First of all, the terrain was exhausting.

The damp ground and piles of fallen leaves require tremendous physical strength just to walk, and the water droplets on each leaf quickly soak your clothes, making your body heavy.

On top of that, the weather was humid and hot, so even a short walk causes sweat to pour down and makes it difficult to breathe.

That was why this dense forest in the distant Western Regions was called the Green Hell.

How could Qing possibly survive the extreme climate of the jungle, where even breathing was a million times more irritating than usual and the discomfort index was at its peak?

"Ugh, this is making my chest feel cold…"

The steel chest guard was extremely cold.

The cold air that usually circulates inside her clothes would normally be emitted from her entire body, but because her chest was tightly bound, the steel has become cold.

\textit{Hmm, I didn't expect this side effect.}

Ximen Qing vs. Tropical Rainforest, 1st round, Ximen Qing win!

However, this was not the only fear of the tropical rainforest.

The tropical rainforest was a paradise for poisonous creatures.

According to scholars from Qing's homeland, the land was lacking in nutrients that the plants evolved to produce poison as a means of survival.

In the tropical rainforest, countless species of poisonous animals and plants threaten humans.

In the jungle, you should never put anything in your mouth unless you know what it is, or rather, even if you know what it is, you should still avoid it, as it may be different from what you know. It was a paradise of poisonous creatures.

That was why the distant Western Regions (omitted) were called a green hell.

"Oh, what's this? It looks delicious."

\textit{A red fruit with an unknown name, is this a cherry? Or is it a wild strawberry?}

Without fear, she popped it into her mouth.

The moment she chewed it, it burst in her mouth, ands he grimaced at the sour, astringent, and spicy taste!

"Phew! Ugh, this is poisonous. It has no taste. Ugh, it ruined my appetite."

Qing searched her pocket and hurriedly took out a piece of dried meat to clean her mouth.

Qing was originally a beggar among beggars and a master at picking up anything to eat.

Poison was just a spicy delicacy, and it can't harm the body of someone with a Blood Poison constitution.

Ximen Qing vs. Tropical Rainforest, 2nd round, Ximen Qing win!

However, the dangers of the tropical rainforest were not over yet.

The tropical rainforest was a world of lawlessness where all kinds of dangerous beasts lurked and the strong preyed on the weak.

Beasts that survive in such an extreme natural environment were naturally agile, cunning, cautious, and relentless, making them difficult opponents for humans to face.

So, the Western Regions, the green hell…(omitted)

Among them, the most dangerous animal was the tiger.

With its powerful strength derived from its heavy weight, terrifying bite, and ability to climb trees with ease, the tiger was the strongest predator and assassin in the natural world, preying on defenseless enemies!

And even now, in the dim twilight, a pair of yellow eyes stared down from the tree branches!

The tiger leaped toward the defenseless intruder who has invaded its territory, kicking with its hind legs to gain speed!

And then, smack!

Crack! Kaah!

The tiger rolled on the ground, letting out a mournful cry.

No matter how thick its skin and muscles are, it was its first time experiencing the pain of a terrifying blow that ignores all defense.

"Wow, a tiger! Shh, be quiet. That's right. Yes. Hey, why are you acting like this? Come on. Hold my hand."

The great tiger's front paw was grabbed by a white hand.

The great tiger, panicked, swung its other front paw, but it was also quickly caught.

Unintentionally standing on two legs, the great tiger stood there holding hands with the human.

The great tiger was sensitive and clever.

Realizing that this strange creature it has never seen before, and one that was incredibly powerful, showed no hostility, it quietly hid its teeth.

"Hm? Calm? What is this? Is it familiar with human?"

Qing strokes the tiger's thick fur.

\textit{It's stiff, yet soft?}

\textit{Hmm, but isn't it the rule that beasts that bite humans shouldn't be spared?}

Qing looked down at the great tiger.

Sensing a slight killing intent, the great tiger immediately let out a squeak, like a cub, and lay down on its back.

Qing shook her head.

\textit{Come to think of it, this isn't a neighborhood where people live, and if you think about it, I'm the one who entered the tiger's territory, right?}

Qing licked her lips, got up, and continued through the forest.

Ximen Qing vs. Tropical Rainforest, 3rd round, Ximen Qing win!

They said that humans cannot defeat nature, but that depends on who you're up against.

At this point, Mother Nature had done all she could. What kind of human being is so strong that they don't know how to tire out,  could regulate their body temperature, and are impervious to poison?

However, the tropical rainforest cannot just stand by and do nothing.

The tropical rainforest's last resort: changing direction!

The tropical rainforest was covered by trees, blocking out the sun.

In addition, it was densely covered with thickets and bushes, making it a natural maze where you cannot see even half a meter ahead of you.

Of course, Qing climbed trees from time to time to check the position of the sun and determine their direction.

However, unless you walk with a compass in your hand, it was impossible to walk in a straight line in the mountains.

Therefore, she gradually lose her sense of direction and veered off course, correcting herself every time she climbed a tree.

Furthermore, Dazhai Mountain was higher in the south and densely forested, so the higher she climbed, the more she was forced to veer north.

Therefore, although she was originally heading west in a straight line, she gradually veered northwest.

Finally, Ximen Qing vs. Tropical Rainforest, 4th round, a victory for Tropical Rainforest! A victory, not a draw!

In any case, she only veered slightly, and Qing was still heading west.

However, let it never be forgotten, that the power that prevents even a master of Harmony Realm from walking straight was the fear of the tropical rainforest.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The mountains of Dazhai were shaped like the Chinese character "子" and surround the north, east, and south of Jinping County.

Therefore, there were two roads leading to Jinping County.

One was a road to the west, where there were no mountains.

The other was a road on the northern ridge, through a gently sloping valley.

If you want to go from Kunming to Jinping County, you must pass through Gejiu and cross Dazhai Mountain.

No one would take a detour of 700 li when the distance was only 200 li.

In other words, if someone wanted to catch someone heading for Jinping County, there was only one obvious place to ambush them.

The northern side of Daochae Mountain!

At this moment, on both sides of the long mountain pass leading to Jinping County, at the foot of the northern side of Dazhai Mountain, there was a group of people who had been sleeping and eating there for almost half a month.

It was truly a foolish thing to do.

Even though the northern side of Dazhai Mountain was a little denser with tropical forest, it was still a terrible place with damp ground and all kinds of insects.

Slap!

"Ugh, damn mosquitoes, I really want to set the whole mountain on fire. Then everything would burn to the ground."

"I just wish I had different shoes. They're so wet from being worn through, my feet feel like they're going to fall off."

"How long do we have to put up with this? Is that bitch Heavenly Blossom Sword coming? Didn't the Blood Cult guys say she was coming?"

"What? You're talking about the enemy of our sect…"

"No, that's not what I mean. Of course, she deserves to die, but I'm just saying that we're suffering for nothing. Honestly, why would a woman who was treated like royalty by the Orthodox sects come all the way here? She's probably eating expensive food at a fancy restaurant right now."

This was quite unfair to Qing.

In any case, given the situation, the initial determination of the Five Poisons Sect sect to burn down the enemy of their sect was dampened by the humidity of the forest, like cotton soaked in water.

Naturally, the leadership was aware of this change in sentiment.

"When the hell is that bitch Heavenly Flower Sword coming? What the hell is going on?"

Five Poisons Sect Leader Hou Tianchi burst into rage.

A few days ago, upon hearing the news that the incoming enemy was Heavenly Flower Sword, Hou Tianchi burst into laughter, saying that the time had finally come to take revenge.

However, the Blood Cult, who promised to lure Heavenly Flower Sword, only replied that they were still searching for her.

Four days have passed since then, and it has been half a month since they set up the ambush, but they have been doing nothing but getting wet in the night dew.

The chief administrator tries to calm Hou Tianchi.

"Brother, please be patient. They say that ten years is not too long to take revenge, so we must endure and prepare for sweet revenge."

"No, aren't you angry, Chief Administrator? Am I the only one who was furious? Our men are suffering greatly right now, and you are calmly saying such things?"

"Of course, I am angry too, but nothing will change if we just keep getting angry. Someone has to remain calm."

He was not wrong.

However, wrinkles appeared on Hou Tianchi's forehead.

\textit{Did anyone get angry at the chief administrator?}

\textit{He should just agree and say that things are shitty, but he always has to say the right thing. Can't we just shut up and get angry together? Symphatize!}

However, it would be pointless to say it out loud, so he just kept his mouth shut and let his discomfort show.

"Let's buy the kids a drink today. In our situation, at least a drink will lift their spirits a little, won't it? I'll take this opportunity to check on the camp, so I'll go around with them. Come on, Elders, let's all go together."

"What if the enemy shows up?"

"It's just a drink. Who's going to get drunk from one drink? Chief administrator, stay and guard the command post. I'll go with the elders. Come on, let's go."

Hou Tianchi said and left the tent.

The elders of the sect followed him, leaving only the chief administrator behind at the rear command post.

The chief administrator sighed deeply.

"Where on earth iss that woman? Ha, I wish she would just show up so we can get this over with and go down the mountain."

He complained in frustration.

However, both in the East and the West, our ancestors always told us to be careful with our words.

It could be a somewhat, or rather, very reckless statement, depending on what kind of flag we raised.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The nostrils of Qing, which had been facing northwest all along, twitched slightly.

\textit{Something smells delicious, doesn't it?}
