\chapter{Rice Blocks (15)}

It was quite a dramatic appearance for Cheolcheonjiwon.

Even the elders surrounding Cheol and the leader of the Five Poisons Sect, Huchonchi, were speechless.

Well, what could anyone say in that situation?

In the middle of Dokyeon, dressed like a beggar, with a pot of rice stuck to his side, frantically shoveling food into his mouth, what on earth could one possibly say?

So when Huchonchi finally managed to utter a single word, it was already after Qing had devoured more than ten spoonfuls.

"…What were you doing right now?"

Qing frowned.

"What, beggar? You're calling me a beggar just because I'm standing here eating rice? No, was it okay to treat people like this? Who were you? Are you someone important? If you're someone important, can you treat people like this when you meet them for the first time? Wow. Mumble, mumble. Hmm, it tastes good."

"……"

Hoo-cheon touched his forehead.

The words he wanted to say were fighting to come out, and his throat felt blocked.

So he held it in for now.

"What was it? Have you never seen someone eat before? What were you staring at? Or were you hungry too? Hey, this was mine! Do your own work, okay? If you're hungry, go cook something yourself."

"……"

Huchonchi held back once more.

He wanted to curse him out and kill him right then and there, but he couldn't.

Why? Because it would lower his status.

You might ask what status means, but for a martial artist, status was very important.

For example, if someone was the enemy of your sect, they must have a certain status.

Whether they were powerful enemies or equally despicable, the enemies of a martial arts sect must be extraordinary.

But the enemy of a martial arts sect was dressed like a beggar?

She has no shame, hugging a large iron pot on the ground and eating noisily and disgustingly, or rather, standing there?

If such a ridiculous woman was the enemy.

If the enemy that the sect must sell its future to kill was such a strange woman?

Wouldn't that make the sect itself worse than her?

In this situation, even killing her was a problem.

At best, we would just become worse than her.

To put it in the language of Qing's hometown.

A mid-sized company sacrificed everything it had, sold its business, sold its office building, sold its cars, betrayed its country, and abandoned its family, all to burn with hatred and wage an all-out war for revenge.

But what if that enemy was just a drunk homeless person who will die alone if left alone?

In that case, winning would be pointless, and losing would be even worse.

Everyone in the world would laugh at them.

Would you consider this a heroic revenge drama in which a group invested everything they had for the future?

That was why Five Poisons Sect-ju understood Qing's intentions perfectly.

Every time he uses a pseudonym, his words and actions were so ridiculous that they were lighter than a feather.

If such a person dies, what then?

It's just a laughable death.

If I abandon my dignity and lower myself, I can make my opponent's end just as miserable and meaningless, a truly laughable death.

But, hmm, they're holding on well…

Should I dig deeper?

Qing once again gazes at the tongue of hell, the intangible torment of the Tang family's certification.

"Hey, you. This isn't even fit for beggars. You're making me feel weak. No, do you really want it that badly? Do you lose your mind when you see food? I didn't know the Oedokmun was a gathering place for beggars. Alright, I'll give you some, but since you're beggars, you don't need bowls, right? Come on, hold out your hands and line up."

It was a cruel insult that made not only individuals but the entire sect look like beggars.

What's more, he said he would share it?

And he told them to open their hands?

He was going to put food on their hands that would kill them?

"Yes, you bitch!"

Finally, one of the elders exploded.

Qing's ears pricked up, but he pretended to be calm and focused, thinking that if they charged, he would beat them to death with a pot, which would make for a good picture.

The plan was good, but Five Poisons Sect was a master of deception.

Of course, it meant that he specialized in cowardly long-range attacks rather than charging.

The elder swung his arms wildly.

He spins his body like a dance, drawing a large circle with his arms, and with a flick of his hands, he fires a barrage of projectiles in all directions.

However, it's just the dance moves of an old middle-aged man, so it's a bit… Well, I thought his dance moves were beautiful when he was young, but what was this, a national singing contest?

Qing plays with the iron pot in both hands.

Even if it's just Ha-Qing's standard, it shouldn't be difficult to pierce an iron pot like this.

But it's a matter of angle.

If you push the dagger diagonally against the corner of the round Chinese pot, it will slide along the curved surface and sink into the thick rice porridge.

Of course, don't forget to rotate the pot so that the porridge doesn't spill out.

With the sound of iron pots clanging, the daggers disappear into the porridge one after another.

"Stop! Elder Sang! Stop!"

Huchonchi's loud voice stops the elder.

As soon as the garlic attack ends, Qing puts the rice porridge pot back on his side.

Then he scoops it up with a spoon as if nothing happened.

"Wow, oh, it's spicier because of the garlic. Munch, munch, gulp. Actually, rice porridge alone was a bit bland, but thank you for adding seasoning."

Qing scoops up a large spoonful of porridge with a special spoon, opens his mouth wide, and eats it.

Then he munch, munch, gulp. Spit!

Then, there was a clang as a small spoon the size of a finger rolled across the floor.

"But the chunks were a little hard. I can't eat this. Hmm, I wish it was spicier. Is there anyone else who wants some?"

"……"

An uncomfortable silence fell upon the group.

He was furious, but more than that, the skill Qing had displayed was truly worthy of being called a divine technique.

Not only did he block all the flying weapons with the corner of an iron pot, but he also ate the poison-coated meat that had been pierced by the weapons?

Am I some kind of immortal?

Huchonchi breaks the silence.

"Cheonhwajam."

"I'm not Cheonhwajam. I'm the strongest bandit leader, Dodokryeon. I'm a rice eater. Can't you see I'm eating rice? Wow. Mmm, delicious."

"Enough of your ridiculous mockery. I already know your true identity, so there's no need to act so arrogant."

Huchonchi lowered his voice.

Qing hesitated for a moment.

He looked as if he was about to write "seriousness" in kanji on his forehead, as if to say that no matter what provocation he made here, it wouldn't work.

It was the intuition of the master of intangible poison.

I had to make my opponent feel as ridiculous and absurd as I did, but if he showed his determination not to react seriously, hmm.

I thought he would immediately flip out and rush at me, but he's surprisingly calm…

"The poison must have already seeped into your spine. How much time do you have left? Are you just going to die like this, making a ridiculous mockery of yourself?"

That poison was being sucked up by the pet bottle of loneliness as it enjoyed its grand feast.

Who in the world could have expected this?

It was too ridiculous to even be a joke.

Qing let out a deep sigh.

Then, I'll have to try another approach.

"No, why are you going this far? Are you trying to destroy the pillar of the sect just to catch me? No, you're just burning down the entire sect. Even if you kill me, I'll still cling to you fiercely."

"I only did what had to be done."

"Well said. I did what had to be done, didn't I? I'm the one who's dying of injustice. I only cleaned up the trash that poisoned innocent civilians, and you're attacking me like this?"

Qing fired back.

"Honestly, shouldn't Five Poisons Sect be grateful to me? Shouldn't you honor me as the savior of the sect for getting rid of its trash? You should erect a statue of me behind the main gate and bow to it every time you see it. You should say, 'Thank you for getting rid of the idiots who would have ruined the future of Five Poisons Sect,' right?"

"Trash?"

"Why, isn't that right? Do you admit it? As a human being, you have to admit it. If you had kept such people as your disciples, it's a miracle that you haven't gone bankrupt yet. I saved the Five Poisons Sect once. Do you admit it?"

However, Huchonchi smiles wryly.

"Trash. Fine. You can think that way."

"Huh?"

"Do you want to argue about right and wrong? The land of Sichuan was originally our Miao tribe's land, and then you Han Chinese invaded and carried out your brutal massacres. How many of our ancestors were driven out to this wilderness, shedding so much blood just to carve out a place to live? Do I have to explain all that to you now?"

\textit{No, you've already said it all.}

Qing looked at him in disbelief.

"Ah, so because it was originally your land, everyone living there now was an invader and can be killed? Because the people living in Sichuan were descendants of invaders?"

"That's how we see it. It may not be the same for you Han Chinese. So even if you call us trash, we won't deny it."

"Are you trying to make excuses?"

"An excuse. Even if this were just a dream and we could go back to that time, I would make the same decision. Of course, that would be after you left Sichuan."

"So what? What are you trying to say? That's not an excuse, you are really trash, so what then?"

"It's just the way the world is."

Huchonchi's eyes were clouded with venom, but they still shone brightly.

Huchonchi was a half-poisoned man.

Poison had seeped into his spine, and all the blood in his body was now poisonous.

However, because he was only half poisoned, his balance was precarious, and he was like a jar full of cracks that could break at any moment.

And now, there was no turning back.

There had been too much anger, and the balance had already been broken by the poison that had been drawn up, to the point where poison was dripping from his eyes.

Huchonchi could not escape death either.

No, he was already close to death.

And yet, he had accepted becoming a half-poisoned man, knowing that.

Huchonchi glanced at each of the Five Poisons Sect elders.

At his gaze, the expressions of the Five Poisons Sect elders gradually became cold.

"I told them to survive at all costs and get revenge. But I will not live a miserable life just to get revenge."

For the sake of our families who have perished, we will not cling to life, but will fight fiercely until the end.

If there was an afterlife, even if it was a hell where evildoers suffer, we will meet again and talk proudly.

We will tell them that we did everything we could for their revenge, and whether we succeeded or failed, there was no reason for the Five Poisons Sect members who have gone before us to be angry.

"We, the Five Poisons Sect, have chosen this path. Right or wrong is not important here."

It was simply hatred.

Huchonchi calmly continued.

"Martial artists are creatures that accumulate hatred, and therefore risk their lives for revenge. This is how we martial artists live, and the cycle of hatred and revenge was what keeps Wulin alive. What is wrong with that?"

Only then did Qing understand the ferocity of the Oedokmun, their blind determination to die rather than die, clinging to life even as they died, and their relentless obstruction.

Oedokmun did not deny the endless cycle of revenge begetting revenge, which begets more revenge.

Perhaps, as the Five Poisons Sect said, the development of martial arts and the martial arts world itself had evolved into something more powerful in order to protect oneself and one's loved ones from the grudges of others.

He did not say that this cycle was bad or unjust.

Nor did he say that the cycle must be broken through forgiveness, as everyone else did without thinking.

He simply accepted it.

And he would devote his life to it.

"Tell me, if your master, your brothers, and your disciples are brutally murdered, will you question their actions, or will you seek revenge?"

"That's…"

Qing's voice trailed off.

Then

Qing scratched the back of her head.

"Aishhh. I don't know if this is right."

Qing put down the rice pot tucked under his arm.

Then he took the water bag from his waist and poured the water he had filled in the kitchen onto his head.

She rubs her face with one hand, and the sound of her skin rubbing against the water was loud and clear.

Now it was completely dark outside.

Suddenly, the campsite was illuminated by the setting sun.

The beauty that rivals the best in the world has washed away the dirt from her face, and her beauty shines so brightly that it lights up the world.

Qing exhaled a long sigh.

"I am Ximen Qing. What happened in Sichuan was a just punishment, and I have no regrets, for it was the right thing to do. Now, step back. Otherwise…"

Of course, those who have already resolved to take revenge with their lives will not step back.

Qing drew the sword at her waist and aimed it at Five Poisons Sect.

"We must settle this in the way of Wulin."
