\chapter{Rice Blocks (16)}

The surroundings fell silent.

It was the quiet before the final battle.

The intentions of Qing pointing her sword were complex.

I'm not sure if this was right.

Everyone easily utters the solemn words that one of them must die for this to end.

It means that they cannot exist under the same sky, that at least one of them must die.

Anyone can say it easily, but very few people actually keep their word. Even among the enemies the blue-clad warrior has faced so far, there were none who have done so, right?

The truth was that people has no intention of dying.

I want to live, but you must die.

So even though they claim to be sworn enemies, when the odds were against them, they immediately look for a way to survive, citing figures like Han Xin and Bu Cha, who overcame crises through servility, to justify themselves.

In contrast, what was the reason why Jing Ke, the first swordsman, became the synonim of chivalrous hero\footnote{俠客; xiake}?

Even though he knew that he would not survive, whether the assassination of Qin Shi Huang succeeded or failed, he still took up his sword and went into battle.

He put his own life on the line for the sake of revenge. This was how one should treat one's mortal enemy.

Even so, were these people worthy of respect?

It was a moment.

An ambiguous moment that can only be described as 'a moment;.

At the subtle moment when the inhalation ended and the exhalation began, about a third of the way through, the enemy began to move in unison.

It was a moment when she was vulnerable in terms of breathing, so it was the perfect time for the enemy to attack.

Blades rushed in from all sides, and he was surrounded on all sides, with murderous intent raining down from every direction.

But they were shallow.

They were just throwing hidden weapons at her.

In fact, even a master would find it difficult to deal with poisoned blades.

But from her position, where the poison had no effect, what else could she say but 'That's all?'

You can increase the power of hidden weapons by imbuing them with your own energy, but the energy embedded in a thrown blade loses its power rapidly once it leaves the hand.

That's only natural.

If that weren't the case, all martial arts would have developed into throwing techniques instead of wielding weapons.

And those who master poison techniques may have powerful poison, but without it, their pure skill was significantly lacking even at the same level.

Qing swung her sword.

A round stream of energy forms around the sword.

It was the pale sunset-color stream of Qi from the Zhu Yang Heart Cleansing Mirror, and it looked as if the tip of the sword was piercing the full moon and lifting it up.

As she swung her sword, the full moon becomes the tip of a brush, drawing thick strokes that envelop the surroundings.

A giant full moon appeared on the ground.

The thick strokes formed a spherical shape, creating a dense sword barrier.

Qing saw Yue Maiden spreading the sword barrier.

The object clenched tightly in her left hand, the headband wrapped around the man's forehead, was the hero's banner.

It was a poorly made object, but it was a token of love that Yue Maiden had made with a needle instead of a sword, for the man who had made her into a human being, into a woman.

And since the man had gone to war and never returned, it was also a memento that had come back in his place.

The enraged Yue Maiden went to war, but the battlefield was nothing but death, death, and more death.

Hatred follows hatred, and countless people hated each other simply because they were enemies, as resentments beget resntments.

Suddenly, a sense of endless emptiness settles in Yue Maiden's heart.

The man who had already left would never return.

'In the past, I was the only one who was happy, but with you, I realized that the world was a happier place because we were together.'

'Now that you were gone and I am alone again, if I had never known you, I would have continued to be happy alone, but because I lost you, I am now filled with nothing but emptiness.'

Standing on the battlefield, Yue Maiden no longer swung her sword at her enemies.

She merely blocked them with her sword.

The world and Yue Maiden were separated.

\textbf{Yue Maiden Sword, 7th Movement. Human Free of Emotion is Hollow.}\footnote{人散情虛; Ren San Qing Xiu}

People faded away and emotions were empty.

The dark energy pouring in from all directions bounces off the sword barrier and flies away.

It was a solid wall that rejects all hostility.

Furthermore, Yue Maiden did not extends her sword toward her enemies. This was separation, and we were futile.

However, this was not Yue Maiden's despair.

Yue Maiden, who rejected the world, was expressionless, but that did not mean she was sad or futile.

She was simply not happy or joyful.

She rejected the outside world and existed only for herself.

That was why she was complete.

At that moment, Qing lowered her sword.

\textit{No matter what, I don't think there was any reason to feel futility there.}

\textit{If my master, my teacher, my friends, and my family at Shinnyo-mun were to die, I would search the entire world to give the responsible bastards the most terrible death.}

Qing suddenly realized.

\textit{Now I understand why I found the Five Poisons Sect men rushing toward me so unpleasant.}

The ferocity of the Five Poisons Sect was the ferocity of men who had resolved to take revenge, but at the same time, they were already dead men who had given up their lives.

Even with their limbs cut off, they clung to their enemies with their remaining limbs. They had no will to live, so how could they be considered alive?

Qing just wanted to give a miserable death to a living evil person and enjoy it with a sense of satisfaction.

She had no interest in cutting up corpses.

But she sympathized with them.

\textit{Is that why?}

\textit{Without realizing it, they tried to make themselves look cool.}

\textit{Still, I can admit that their determination to seek revenge is admirable.}

But she was also curious.

What if all that determination, all that evil, all that revenge was nothing but suicide?

What if they realized that with their inadequate abilities, they couldn't even achieve revenge, not even a small wound, nothing at all?

Would you still say that you have no regrets because you devoted your life to revenge?

Could you really say that?

\textit{If you come back then and lament and grieve.}

\textit{That's fine.}

\textit{We should go back and enjoy it again.}

\textit{If you can accept that what matters iss that you devoted your entire life to revenge, even if the result iss not what you wanted, then you will remain confident until the very end.}

\textit{Then maybe my petty whims were worth it after all.}

The full moon setting on the ground disappeared, and between them, a beautiful woman of unparalleled beauty appeared.

The Five Poisons Sect paused for a moment.

The technique of building a wall with swords was in itself a very difficult and advanced skill.

But to surround oneself with a spherical wall? How powerful must one's Inner Qi be to achieved such a level?

Meanwhile, the Moonlight Sword moved again.

A large sword swung lightly up and down, left and right from its position.

The flow moved from the arms to the shoulders, the shoulders swirled and became more elegant, from the shoulders to the waist, the waist twisted and bounced, creating an even larger movement, from the waist to the knees, the knees rose and fell in rhythm, from the knees to the toes, the toes lightly touched the ground and move forward and backward, spinning and twirling, sometimes advancing and sometimes retreating.

The swings of the sword spread throughout the body, which responds in kind, creating a dance.

A single dance movement, a sword dance performed with a sword.

The eyes of the Five Poisons Sect members were filled with confusion.

'Surrounded by enemies on all sides, why is she dancing?'

However, it was also a breathtaking sight that could not be seen again in this world, making it impossible to look away.

The white face, shining alone in the dark surroundings, must have been exceptionally beautiful.

The dance of a beautiful woman had a magical power that captivates everyone, regardless of age or gender.

Suddenly, a strong wind, carrying a clear energy, rushes toward Qing as if being sucked in.

"What are you doing? Attack! Stop her now!"

When Hou Tianchi shouts, the elders of Five Poisons Sect and the disciples outside hurriedly put their hands inside their robes.

Then, flowers bloomed and swirled around.

Following the blade wielded by the beautiful woman, colorful petals swirl around.

All the energy in Qing's dantian bursts out at once, revealing itself to the world in various colors.

Some were golden yellow, slightly reddish in the sunlight, shining brilliantly, but somehow resembling the luster of a Buddha statue.

Some were so white they seem to be veiled, and the less white ones were cool and refreshing.

Some were deep blue, imbued with the loneliness of the sea.

The peach blossom color holds a breathtaking allure.

Then there were the red ones, some with a cruel smell of blood, others with the innocence of a child, and still others… Well, most of the demons were similar in color, so it's hard to tell them apart.

\textbf{Solitary Nine Swords, Eight Movement. Countless Changes.}

Of course, if Celestial Martial Emperor saw this, he would laugh in mockery.

'No, what kind of Countless Changes is that? I never created such a poor technique, so if you're going to imitate it, at least do it properly.'

'If you say you learned it from me, I'll be embarrassed, so call it's something else, not Countless Changes.'

'Yeah, Thousand White Changes, no, Thousand Blood Changes would be more accurate.'

\textit{Well, it's a cheap imitation, what can I do?}

\textit{I can't just go all out like I used to and end up collapsing with multiple fractures, muscle tears, and organ damage.}

\textit{At least my body was transcending Harmony Realm, so I can at least imitate Countless Changes. Wow, but even this makes my dantian ache and my Qi meridians burn.}

\textit{How the hell did I even use this at Peak Realm and survived?}

Qing internal energy was draining out in chunks.

It may seem strange that hundreds of strong winds, which were only used for lighting and deception, were not being dispersed.

Death was raining down from all sides.

It's not to the extent that the whole world was filled with flower petals like Celestial Martial Emperor intended, but rather like when you kicked a flower tree once and the petals fell down.

Even so, those petals couldn't maintain their momentum, and once they passed a certain radius, they flew straight ahead like arrows.

The elders were able to deflect them with their weapons, but for the disciples, it was a disaster.

"Damn it, Elders! Let's go!"

Huo Tianchi shouted as he rushed forward.

The distance he had opened up to throw their weapons was now coming back to haunt him.

Although each petal was beautiful, it's power was something that could only blocked at Peak Realm.

Of course, it would take a long time to block them all by picking off one or two petals at a time, but that was the nature of the attack.

It was only natural that the power of the wide-area attack was weak, even in Qing's homeland.

Therefore, it was time for the masters to get close and block the attack.

First, they had to block the dance moves, and then they could knock away the petals, but if they just kept blocking until the enemy got tired, they would have no chance of winning.

In fact, it was better to just block the attack.

Because Qing's Inner Qi was shrinking rapidly.

\textit{Wow, half of them is gone in an instant.}

\textit{It's embarrassing to stop because I'm running out of strength, so I'm glad that you rushing in.}

Five Poisons Sect may feel wronged, but how could they know how long this technique would last?

In an unknown situation, the couldn't take the risk of letting ordinary disciples die.

Ka-bang! The flowing sword were blocked by several weapons.

The weapons were different, but they were all held in the left hand, which seems to be a characteristic of Five Poisons Sect's martial arts.

Qing immediately stopped her spinning body and extended her left hand to lightly push the elder's chest.

The result was not light.

Deeng…!

With the sound of a temple bell, the elder spit blood from his mouth and fell backward.

His chest was caved in, and he vomitted pieces of his torn intestines along with blood.

At the same time, the momentum of the Moonlight Sword changed.

The sword, which had been floating weightlessly as before, suddenly becomes as heavy as a mountain and struck down with brute force, slashing left and right and striking with the flat of the blade.

It was the overwhelming momentum of the Ximen Surin-style Divine Maiden Sword.

As if to say, 'Do you think a woman is weak? Never underestimate a female swordsman again.'

Qing swiftly swept through the enemies.

Except for Sect Leader, there were eleven left. She caught one, so there were ten left, which means eleven remaining.
