\chapter{Rice Blocks (4)}

The Ten-Faced Ambush Plan. In the previous story… (omitted).

Anyway, it's complete!

The elaborate personnel deployment and communication system, which divided up an entire mountain ridge, was a masterpiece completed with the help of outside "experts."

However.

The Ten-Faced Ambush prepared by Five Poisons Sect and assisted by the Blood Cult was not just a large-scale encirclement operation.

In addition to the ambush, formations were created using natural objects, creating a labyrinth that twisted people's internal defenses and perceptions, making them wander aimlessly.

If you didn't know the secret passages and gates, even if you tried to break through by force, you would end up going around in circles, and if you let your guard down even for a moment, you would lose your companions who were nearby.

In the end, those who fell into this trap would be scattered and face countless enemies rushing in from all directions.

That's not all.

No, rather, the most deadly, powerful, and dangerous part of this ambush remained.

Since its founding, the Five Poisons Sect had been stockpiling a huge amount of poison, and now they poured it all out!

Sects that deal with poison have many enemies.

The Five Poisons Sect was no exception.

If someone died from Five Poisons Sect's poison, the Five Poisons Sect would inevitably be blamed.

It didn't matter if the poisoning was the work of Five Poisons Sect or not.

Whether it was something sold by the Five Poisons Sect, something sold decades ago and completely unrelated, something that wasn't even sold and was stolen, or even a different poison with similar symptoms that was mistaken for theirs, it didn't matter. They hated the Five Poisons Sect.

And that's not all.

Let's say that Five Poisons Sect won a fair fight between members of different sects.

If this were a normal fight between members of different sects, there would be no hard feelings, as this was the way of Wulin.

But what if poison was used?

Even if the poisonous sect wins, not only will they be pointed at for using dirty tricks, but their enemies will also refuse to accept defeat and hold a grudge.

That was why the poisonous sect was so cruel.

It was not for nothing that they live by the saying, 'We will repay kindness with double kindness, but grudges with tenfold'.

If the poisonous words fail to instill fear, the hatred accumulated over time will rise up and crash through the walls.

And this fear stems from the poison itself, from the vast reserves of extreme poison stored in that warehouse.

Did they pour out all those poisonous reserves?

It would not be an exaggeration to say that the future of the Five Poisons Sect was completely destroyed in this one ambush.

However.

There were things in this world that had to be done, even if they were foolish.

This ambush was one such thing.

The Five Poisons Sect lost more than half of its most precious disciples in the Sichuan disaster.

Even the senior disciples of the first generation met a terrible end.

To resolve such a grudge, they must give up the very future of their sect.

Furthermore, since they were involved with the Blood Cult, if this fact was revealed, they will be attacked by the entire Zhongyuan and their sect will be destroyed.

In effect, Five Poisons Sect had given up on its future.

The Five Poisons Sect's grudge was so deep.

That's why this ambush was even more frightening.

A sophisticated plan designed by experts. Formations added to that. And then, they poured in a generous amount of deadly poison.

And the final element that adds the finishing touch.

It was this grudge, or rather, their fighting spirit!

No matter how perfect an ambush plan is, without the fighting spirit of its members, it was like a loose net, and the enemy will slip through like a fish.

The fighting spirit of those who rush fearlessly at the enemy, caring nothing for their own safety, biting their arms if they were cut, and wrapping their legs around the enemy even if their jaws were broken, in order to hold them back!

And that was exactly how the Five Poisons Sect was now.

Having given up even the future of their sect, these people, who had given up on tomorrow for the sake of today, wanted nothing more than to kill their enemies.

Now that the terrifying ambush was perfectly prepared, all that was left for the Five Poisons Sect was to wait for their unsuspecting enemies to walk right into their trap and meet their terrible end… Or was it?

But their enemies did not come.

There was no news at all.

They had sold the future of their sect to set this trap, but their enemies did not come.

All the members of the sect were eating and sleeping outside, exposed to the dry wind and cold dew, even spending the night outdoors…

"…Where are they?"

"We have not found them."

"What do you mean?!"

Bang! Sect Leader Hou Tianchi slams down his large desk.

"Are you saying they've risen from the ground or disappeared into the sky? Didn't you say they were heading for the mainland? Then why haven't we seen a single one of them yet?"

"Sect Leader, please calm down. They're just young kids, aren't they? They're probably just sightseeing in Gejiu…"

"No, sightseeing at a time like this! Why on earth! Why don't they just come right in!"

"Well, they're not coming to fight, so there's no reason for them to rush. Besides, Gejiu is such a spectacular sight…"

\textit{Yes, the terraced rice fields of Gejiu is a spectacular sight… No, that's not it!}

Hou Tianchui found himself agreeing, and his teeth gritted in frustration.

In fact, he was not angry at the Chief Administrator.

And the Chief Administrator must be just as frustrated, so Hou Tianchi had no choice but to grit his teeth.

Still, he can't help but feel disappointed.

"The Blood Cult guys haven't said anything? If they're hiding something…"

"They are very cunning. They only say that they will arrive soon."

"our disciples have already spent five nights sleeping outside. Tsk, let's give them a special meal today. But we must not let our guard down. And also…"

And so, Five Poisons Sect continued to spend the night outside.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Five Poisons Sect, Main Hall.

Even though all the disciples were out on ambush and Five Poisons Sect was empty, there was a strange heat flowing from the center of the Main Hall.

Originally, this was where the Sect Leader and the Elders discussed the affairs of the sect, so now that they were all out, it should have been empty.

Surprisingly, on the large desk where meetings were held in the main hall, a man and a woman were engaged in sexual intercourse.

No matter how much they were considered the scoundrels of the sect, such behavior was unimaginable.

How could such obscene acts be committed in the center of the sect, the most public place?

This was tantamount to insulting all the ancestors of the sect, and was a terrible mockery that would result in Senior Brother being sentenced to death for destroying the sect precept, or having his dantian destroyed and his meridians severed.

However, as long as nothing was discovered, there would be no problem.

In the Five Poisons Sect, where there were no Five Poisons Sect disciples, how could anyone know and be angry if someone made rice cakes or roasted a pig in the sacred main hall?

However, the person who was engaged in the intense orthodox and unorthodox practices at that time would not have cared even if he had been caught.

That's because he was a member of the Blood Cult, one of the most powerful members, a poisonous demon who led the Blood Cult's executioners, the group leader of the Blood Cult.

This was the average personality of the Blood Cult guys.

On top of that, it was a scene that was difficult to look at with a sober mind.

There was a boy who looked immature, and an old woman.

It was a terrifying situation that cannot be described in words, and should not be described!

As time passed, it became more and more intense, and then…

At that moment.

"Poison Demon, we're in big trouble, ugh."

The Blood Cult warrior who pushed open the door froze in his tracks when he was hit by a visual attack he could never have imagined.

"What is it? What's all the fuss about? Can't you see I'm busy?"

Poison Demon's attitude was perfectly calm.

Rather, it was the old woman who had been rolling around with him who was startled and quickly hid herself.

Poison Demon smacked his lips.

"There's no need to be so scared. If it's that urgent, you wouldn't have dared to rush into my presence. So, what is it?"

The reason why the Blood Cult warrior was trembling was a little different.

Poison Demona was a very practical man, and if they had been polite, he would have been angry at their lack of urgency.

Even so, the Blood Cult warrior was afraid. Where would you find a man who wouldn't be afraid after seeing that?

\textit{I had heard rumors about Poison Demon's tastes, but I never thought it is true…!}

"That's it, that's it, the poison factory was attacked. The mine was buried, and all of Zheng Mansion's comrades were wiped out. There were five survivors, that's all."

"What?"

Poison Demon's expression crumpled.

"What about Sejeong?"

"Sejeong was dead…"

At that, Poison Demon's expression became irritated.

\textit{How much time does it take to raise a single disciple? I thought I had finally trained a smart kid who could do the job, and now she's dead?}

"No, how dare they? Who was it?"

"The perpetrator was said to be the strongest bandit, Tudulian, who is believed to be a master of Harmony Realm."

Poison Demon's expression became even more distorted.

The strongest bandit? Who would use such an alias?

A rice-eating bandit?

Not only was it incomprehensible, but if a Harmony Realm maste had such a ridiculous alias, they would have been even more famous for it, yet Poison Demon had never heard of it before.

And Tudulian?

The name Dulian was very beautiful, but it's not a name you would give to a child with the surname Du.

It must be an alias and name given by a master who was hiding their identity.

\textit{But who?}

\textit{Well, we'll just have to find out by beating them up ourselves.}

\textit{They dared to touch my disciple?}

Just as Poison Demon was about to speak,

"Also, Young Master Zheng and warrior Dong were seriously injured…"

"What?"

"Their condition is not good."

"No, why are you reporting that to me? You should call that jiangshi and tell her to report it to the Sword Demon."

"Their condition are very serious. They have lost their eyesight and hearing, and their tongues have been cut out…"

"So report that to Sword Demon. Ah, wait a minute. Oh. They were quite skilled chivalrous warriors, weren't they? Hmm. Hmm. I was wondering how to deal with those who dared to touch my men, but that's fine."

Poison Demon hurriedly put on his clothes.

"Go tell Jae-ryun. I'm leaving right now, so gather some suitable men. And, um, tell Sword Demon too. I'll send Tudulian to the same fate, so consider it a debt he owes me. Now, let's go."

It was at that moment.

A slight breeze blew, and before I knew it, a strange woman appeared in the open doorway.

"Oh, Poison Demon. Wait a minute. Are you done with that horrible act?"

"What are you talking about, you jiangshi? And what do you mean, horrible act? You may not know this, but sharing love between a man and a woman is not a horrible thing at all."

"But you're old!"

"So, at my age, I have to roll around with a young girl? An old man like me sticking to a young girl, isn't that terrible?"

"Oh? Is that so? Anyway. Hmm."

The woman pretended to clear her throat.

Then she raised her voice.

"The Chairman has given his orders. There has been a rebellion in Nanyue, so Poison Demon must go and deal with it himself. That is all."

"What? Why now of all times?"

"The order came down a while ago, but Poison Demon was so absorbed in his work that I didn't dare approach him, so I waited here."

Poison Demon frowned.

"If it was an order from the Chairman, you should have told me first. Hmm. Then, what should we do with Tuludian?"

If he left someone of Harmony Realm to his subordinates, they would surely get killed or injured.

If they were just mindless brutes from another unit who only knew how to swing weapons, it wouldn't matter, but the children of his Blood Poison Corps were well-rounded, skilled in both martial arts and academics, and have so much to study that they were difficult to raise.

After a moment of thought, Poison Demon suddenly snapped his fingers.

Isn't there an old saying, 'Use their own weapons against them'?

"Alright. Let's have the Five Poisons Sect guys deal with them instead of our kids. Release the reserve troops that the Sword Master sent and lure that woman to where the Five Poisons Sect guys were ambushing her."

"But will the Five Poisons Sect guys agree to fight them? They were so eager to capture their own enemy."

"The Five Poisons Sect's greatest enemy is Heavenly Blossom Sword, right? Then tell them that the identity of Tudulian was Heavenly Blossom Sword. They will rush in to kill her. If they say later that it wasn't her, we can just say that we are also deceived."

Now that he thought about it, it was a good plan.

\textit{The Five Poisons Sect guys will be furious, but they're the ones who lost, not our cult.}

However.

It's like a cow trying to catch a mouse by backing up.

If Qing knew, she would have been very upset.

Or maybe it's better this way.

If they didn't run away and attack her, she might even welcome them.
