\chapter{Rice Blocks (2)}

Qing smiled in front of Dong-joo, who was glaring at her fiercely.

\textit{If you had to visualize angger, isn't that the exact the expression?}

\textit{If you could kill someone with just an angry look, wouldn't you feel like you had to kill them?}

\textit{Of course, an enemy's anger is the highest compliment.}

\textit{Now, come on, attack me.}

However.

"Ugh."

"Young Master. I'm sorry. Please bear with it a little longer."

His hands trembled with humiliation, but he carefully put down Zheng Liuzhang and began to untie his clothes with even more careful hands.

Qing's expression turned sour.

She was just immersed in her role, saying it was a feast for the eyes, but now she had to watch a man undress, and even a man undressing another man?

\textit{I can't watch this…}

\textit{Yes, there will be a momentary technical difficulties notice at the screen.}

Qing focuses her gaze beyond the two men, far away, on the black column of smoke still rising from the mine in the distant sky.

\textit{Still, the fire should go out quickly. Surely it won't continue to burn underground like that mine that burned forever?\footnote{Coal-seam fire, the most famous being Centralia mine}}

\textit{If it turns into a big problem, oh no, what will happen to Zhuge, who took full responsibility for the fire at the mine?}

\textit{Zhuge, all I can do is pray that the fire is extinguished quickly, but still, I believe that with the power of the Zhuge Clan, one of the Five Great Families, you will be able to overcome this.}

"Are you satisfied now?"

"Oh, what the heck. I didn't think you'd actually take it off when I told you to."

"What?"

Dong-juk's face immediately turned red.

Regardless, Qing waved her hand.

"That's enough. Just go. I was looking forward to wielding my sword for the first time in a while, but you're a man with no pride."

In Qing's homeland and Zhongyuan, the way to humiliate a man had been the same since ancient times.

How could Dong-jook not raise his voice?

"…The strongest bandit, Tudulian, someday you will regret this moment with all your heart."

"Hah, this Tudulian have no regrets in my life. Well, maybe one. I should have made you a man in the first place. What was I thinking, looking at your back and chest? Anyway, be grateful."

"What?"

"The famous general of the past, Cao Hong, said that frustration makes a man. Remember today's humiliation and engrave my name on your worthless pride. Work hard and improve yourself, and it will become the driving force for your growth."

Dong-juk, who couldn't hide his resentment, frowned as if something was bothering him.

"…? Did Cao Hong say that? I've never heard that before."

"Huh? No? Was it the opposite? That a man should succumb to his frustration? Something's strange."

"From now on, it would be better if you don't loiter around Yunnan."

\textit{This guy again. He's not going to say let me have the last word.}

Instead of answering, Qing shrugged her shoulders and stepped slightly away from the road.

"Young Master, excuse me."

"Aah!"

"It's Dongjuk. Young Master, calm down."

Qing's gaze as she looked at that scene was colder than the harsh north wind on the coldest night of winter.

He was sitting there looking like a complete fool.

The gruesome scene of the poison factory in the underground mine flashed through Qing's mind.

It was different from the disgusting scenes that Heavenly Slaughter Star sometimes showed.

It was a fragment of the real world, right before her eyes.

It was exactly as the saying went: 'A sea of blood and a mountain of corpses'. The stench that pierced her nose, the damp air filled with the scent of human blood, the countless bones, the melted flesh, and the rotting remains piled haphazardly…

\textit{The creatures who had caused the deaths of hundreds of innocent people are now naked and embracing each other. Ugh.}

\textit{It is a truly pitiful sight.}

\textit{I wish those Blood Cult members had at least had some sense of loyalty and affection for each other.}

\textit{If they had just fought to survive on their own, pushing and shoving each other aside, begging for mercy, it wouldn't have been so disgusting.}

\textit{If it had been such a pathetic spectacle, I could have just laughed it off and said, 'Yeah, that's what you deserve.'}

Dong-joo hugged Zheng Liuzhang, pointed the sword in his right hand at Qing, and cautiously took one step, then another, closer to her.

As he covered Zheng Liuzhang with his body, Dong-joo's body gradually tilted sideways as he got closer.

Finally, he took a sideways step.

"Wait!"

Qing shouted, aiming her Moonlight Sword.

"What? Now you're breaking your promise—"

"No, wait. What is that? You, you… He's acting like a child. I didn't see that wrong, did I? You…"

"What?"

In an instant, Qing unleashed a fierce Sword Thread.

Her gentle gaze was nowhere to be found, and she suddenly exuded a sharp killing intent.

"How! You bastard! You cruel monster! How can you do such a thing while wearing the mask of a human being! You gouged out his eyes, his ears are bleeding, and you made him unable to speak! How could you do this to a person! Are you really human!"

Qing shouted.

If Zheng Liuzhang's eardrums had been working, it would have been so shocking and absurd that he might have burst into tears.

'How dare you say that after what you've done!'

However, fortunately or unfortunately, Zheng Liuzhang's eardrums were completely opened, so Dong-jook jumped up in indignation instead.

"Wait, I didn't…"

"No questions! I may be a mere thief, but I will not turn a blind eye to such a terrible evil! No matter how deep the grudge, one cannot dare to make a person suffer so miserably!"

Qing's were confident in her words.

People should not be treated that way.

But what if they were not human, but animals?

In fact, the more evil they are, the more miserable they should be made to live, so that the people of the world will see and be wary.

And if there was an afterlife, the innocent who have already died and were shedding tears of blood will look down and feel a little better.

Qing held her Moonlight Sword straight.

Dong-joo was terrified and swung his sword, and then, bang!

The swords collided, and the colors of the Sword Thread flew like sparks.

Dong-joo's expression froze noticeably.

It was only one blow, but the superhuman strength behind it made his wrist tingle.

He was wondering why a woman would wield such a large sword, but it turned out she was female warrior with great strength.

"Wait! This is a misunderstanding!"

"What misunderstanding! Die, you villain!"

Dong-joo took a step back and managed to block the sword.

Each time they collided, his wrists ached, and eventually, an unusual pain began to pierce him.

In contrast, Qing, who was wielding a large sword with both hands, seemed to be swinging a light piece of wood rather than a piece of metal.

The sword he strikes away stops in midair and moves in the opposite direction at the same time.

It was as if time was flowing backwards.

In a fight between martial artists of the same level, female martial artists were usually at a disadvantage.

Even if they were equally skilled, a woman would inevitably suffer one-sided damage due to her lack of strength and weak bones every time their weapons clashed.

However, now it was completely the opposite.

Even among women, female martial artists who were born with exceptional strength and physique were considered to have almost no flaws.

The softness and flexibility unique to the female body, the long strides that come from longer legs, and the unpredictable changes in height that come from the high position of the pelvis…

Even when fighting with full strength, it was difficult to win against such an opponent, let alone when fighting while hugging them with half your body to protect Zheng Liuzhang.

"Wait, it's a misunderstanding! It wasn't me!"

"You coward! Now you're lying! Can't you admit it like a man?"

"No! It's not true!"

"A strong denial is a strong affirmation! Come on, you're finally confessing!"

"No! It's not true!!"

That was the moment.

Qing, who was about to thrust her sword again, suddenly bent her knees and sat down.

Her buttocks almost touched the ground, and her long legs were bent in half, so from Dongjuk's perspective, she suddenly disappeared from his field of vision.

It was a moment when his heart seemed to stop!

"Die!"

Pah! Qing's leg drew a semicircle, grazing the ground.

Qing's toe rushed toward Dong-juk's ankle like a lightning bolt.

That was the moment.

Dong-juk desperately stretched out his leg, dragging it roughly across the ground and kicking up dust, pushing Qing forward.

Pah!

Dong-joo's lower body, which was caught by Qing's ankle instead of toes, was lifted high into the air.

Dong-joo's body was now horizontal, parallel to the ground, and his horrified face, lying sideways, did not take his eyes off Qing.

Unfortunately, in the process, Zheng Liuzhang slipped from his grasp, and the men who had been huddled together in a group were separated into two, rolling around on the floor separately.

Qing was slightly impressed.

\textit{Oh, he knows how to fight?}

\textit{If my toes had hit the bone at the ankle, it would have been shattered into pieces and left him limping.}

\textit{If he had stepped back or jumped up, I could have just followed his trajectory, but instead, he took a step forward and tanking the hit.}

\textit{In terms of combat intelligence, he's the kind of talent who could reach the highest level if left alone.}

\textit{But is there any point in playing with him anymore?}

Dong-juk, who was about to get up in a hurry, suddenly froze in place when he saw the sharp blade heading toward his chin.

"You despicable villain, beg for forgiveness from that poor young man before you die."

"It's a misunderstanding. Please, Hero, hear me out."

"Ha, you call a mere bandit a hero? You become servile when death is upon you. That is truly the nature of an evil person."

"No, I can explain everything…"

"Ha ha, what a ridiculous last words! Accept the judgment of justice quietly!"

Qing shouted loudly and raised her Moonlight Sword high.

In that moment, Dong-juk's eyes flashed!

"Die! Cry out, Moonlight Sword, rain down!"

The Moonlight Sword slashed vertically through the air and fell.

Then, bang!

There was a loud clanging sound, followed by the sound of something heavy spinning, and then a thud. The sharp blade of the Moonlight Sword flew through the air and stuck into the ground, standing alone in a beautiful pose.

"Huh?"

Looking at her empty hands, she uttered a question in confusion.

Dong-joo stood up abruptly and raised his sword with a sinister smile on his face.

"You bitch. I'll kill you."

"Wait, wait! I don't have a weapon!"

"How dare you be so insolent. I said I would make you regret it."

Dong-joo began to swing his sword.

Now, he no longer has his young master to hold onto, nor the baggage, and the woman he wanted to kill had no weapons.

Then, red Sword Qi draws countless trajectories in the air.

"Waaah! Waaah! Wait! Talk! Talk! Talk! I said let's talk! Waaah! Waaah!"

"You're dodging well! Die! Die!"

"Hey, wait! Wait! Waaah! Wait, you grazed me! You grazed me! That's a foul, a foul."

Dong-Juk's sword technique, when executed properly, was a vicious killing sword technique overflowing with killing intent.

However, between the Sword Qi that cut through everything, Qing skillfully rolled, jumped, dodged, retreated, crouched, and bent, dodging them as if it were a precisely coordinated martial art.

The speed was so fast that it seemed as if multiple Qings appeared and disappeared at the same time, moving as if they were fighting in midair.

Then, bang!

Qing stepped back and created some distance.

"Wait!"

"You want to talk now? It's too late. I'll kill you for sure!"

"Let's make a deal."

"A deal?"

"Yes. If you back off, I won't chase you anymore, and I won't hold a grudge against you. I'll let you go with no hard feelings. Oh, of course, you already look pretty cool as you are. No taking back, you know? You already gave me your clothes, so they're mine now."

"Still running of your mouth? I'll kill you and keep your mouth for myself. Let's see if you're still so loud when you're dead."

"Wait! If you want to continue fighting, I, the strongest and most powerful bandit, will fight with all my might! I won't go easy on you anymore!"

"Ha, really? You'll go easy on me?"

"Yes! And when that time comes, no matter how much you cry and sob and wipe away your tears and snot and rub your palms until they burn, I will never forgive you. This supreme bandit will never let anyone who has witnessed my skills live! Now, quietly pick up your handiwork and get out of here. This is the last chance I'm giving you, especially for you!

However, Dong-joo just smiled wryly.

\textit{Her movements was impressive, but she's still hiding her true abilities? Even a ten-year-old kid wouldn't fall for that.}

"Really? I'd like to see your impressive abilities."

"Really? This is your last chance. You better take my offer while I'm being nice. I'm gonna show you my true power. And I'm not gonna let you go. I'll kill you for sure."

"Hah! That's a funny last will and testament!"

"Huh."

Dong-juk burst into laughter and swung his sword again, its blade flashing with blood-red Sword Qi.

And then, thud.

Qing's long, white fingers, transparent and beautiful, lightly held the blade.

"What?"

"Ah, I see. I wondered why you were hiding your strength, but now I understand completely. How can I resist this? In that case, I'll accept my defeat!"

"Wh-what?"

Dong-juk was taken aback and pulled out his sword, but Qing's hand clenched into a fist and held the blade firmly in place.

Dong-joo's arm trembled as he desperately infused his True Qi into the sword and pulled with all his might.

However, the sword remained stuck in place.

Then, there was a screeching sound.

Finally, Qing's fist closed completely.

Dong-joo shouted in shock as he pulled the sword.

The broken sword blade fell to the ground.

When Qing opened her fist, the twisted piece of metal fell onto the dirt road.

This was the difference between the levels of Peak Realm and Hwa-kyung.

It was the difference between the eyes of peak Realm and Hwa-kyung.