\chapter{Rice Blocks (9)}

Pasa… The sound of the forest swaying in the wind was like the crashing of waves.

The flow brushing against her skin, Qing's sensitive senses read the changes in some great flow.

The wind was changing.

And it was very unnatural.

Qing's sensitive senses sensed something unknown and indescribable.

\textit{Something subtle, something… What is it? The flow I sense in the air seems slightly different from what I see and hear. Ugh, I feel like I'm going to get seasick…}

Illusions and delusions had no effect on Qing.

However, the 64 Seals of Heavenly Chaos, which distorted the energy of heaven and earth and confused the senses, were closer to the principle of obedience than to reversing the flow.

Therefore, Qing was only partially affected by the true technique.

If she had been completely affected, she would have considered her distorted five senses to be normal, and if she had not been hooked, she would not have been affected at all.

Being only partially affected, her sensitive senses became poisonous.

It was ambiguous to call it poison, but-

If the phenomenon of dizziness caused by heightened senses not being fully affected by the true technique was considered poison, then the creators of the true technique would be unjustly blamed.

Her head aches slightly, and her stomach churns, so she took a deep breath.

But the damp wind, heavy with moisture, shakes the cold air around Hansim Gong and clung to her, spreading a dirty warmth like a stain.

\textit{It's sticky and stuffy…}

Qing looked down at the old man's head. His face was frozen in a smile.

\textit{For some reason, I don't like it. I really don't.}

\textit{What did I do to deserve this?}

\textit{He really did it, he really did.}

Qing lifted her foot.

\textit{One kick from Heavenly Demon Reigning Steps (very powerful) and his head will be smashed into a pile of bloody debris like a broken watermelon.}

But then, she sighed.

Qing enjoyed the suffering of evil people who were still alive, but she had no interest in desecrating dead bodies.

But she couldn't help thinking about the head.

\textit{He could have saved his life if he had begged for mercy.}

\textit{Of course, I would have confiscated the limbs, but I could have let the old man enjoy the spectacle of his efforts being wasted, watching Five Poisons Sect being destroyed from the front row.}

\textit{So, why am I feeling bad?}

\textit{But the old man died smiling, so I guess he felt satisfied in the end.}

\textit{Then, um, doesn't that mean I lost?}

\textit{Ugh, this feels uncomfortable.}

Qing scratched the back of her head loudly.

\textit{Well, whatever.}

\textit{Let's see what kind of trap they prepared.}

Qing stretched her limbs.

\textit{If there are no witnesses, it's assassination. The dead can't speak. If I kill everyone here, both Tudulian and Heavenly Blossom Sword will be out of the picture. I could go scout out as Xiatian, but I already used her for the Blood Sect.}

\textit{Two, two, turn your arms, turn your waist… Is it the national exercise routine? Or the safety exercise?}

\textit{Safety is good, good, good, good?}

Qing relaxed her body and pricked up her ears.

The sound of leaves rustling.

It was the sound of footsteps gathering from all directions.

And then, at that moment.

Qing covered her face with her hands.

A needle about three inches long was caught between her index and middle fingers.

A tiny hole was pierced at the tip of the needle. A minute drop of liquid hung from the needle, trembling slightly.

"Who are you! I am the rice eater, the strongest and most powerful bandit Tudulian! The strongest does not hide or run away. Come out and face me!"

It was a passionate speech full of courage.

But instead of an answer, only the needle made a sharp sound.

"No, you're using sorcery! Only despicable, sinister, and evil people use such sorcery!"

'Sorcery?'

Even those who heard it felt their stomachs turned.

The invisible poison of Qing's mouth was victorious once again.

"There!"

Qing stomped on the ground.

The effect of the Heavenly Demon Reigning Steps was tremendous!

As if a cannonball had fallen, dirt and leaves flew up in all directions.

\textit{Master, please allow me to become a righteous thief, a divine avenger, today. I will take the lives of evil people and make this world a better place.}

If Tian Youxue had heard this, he would have been furious, asking why a Divine Thief would steal lives.

But Tian Youxue was not there.

The only thing there was the smiling head of the old man with the red mark, which rose up along with the ground.

By coincidence, Qing's and the old man's head locked eyes.

\textit{Ah, you're granting me permission!}

\textit{He's not my master, but he's still an old man like Master, so he must have about three-quarters of the same traits.}

\textit{Then, mathematically speaking, I've been granted three-quarters of the permission.} (No, that's not right.)

The arms crossed in front of her head collide with the hidden weapon, making a sound like metal hitting the ground.

\textit{These are bulletproof arms! Where are you going?}

With a rustling sound, she broke through the bushes and comes face to face with Five Poisons Sect, who looks completely flustered.

Each joint of the hand held aloft was pierced with long needles. It was what Lan-Ah was doing, but well, the method of throwing needles was pretty much the same.

The new-style sword of the blue-clad figure swirled through the air.

The cheap helmet was torn off and flies away, and suddenly, a rear leg extended, the heel struck like an axe blade, crashing down on Five Poisons Sectdo's shoulder.

Pazak, the sweet sensation transmitted through the heel, a tingling current like electricity running up the spine, brushing past the back of the neck—Ah, back of the neck!

The Five Poisons Sect's member, who had landed on his buttocks, clutched his shoulder and spoke in a trembling voice.

"What—"

"Good! And you, become my comrade!"

"What—"

Instead of answering, Qing quickly reached out her hand.

He grabbed Five Poisons Sect's member's left arm and rose up silently with an elegant movement.

It was Yue Maiden Steps' anti-gravity walk.

Qing shouted in alarm at the countless rustling sounds coming from all around him.

"Look, this kid is now my shield! Can you shoot now? Do you have the guts to shoot you family?"

"Shoot, shoot! I don't care, you villain."

Surprisingly, the one who answered was the Five Poisons Sect's member, who had turned into a meat shield.

It would have been cool if he hadn't bitten his tongue.

"I don't care! I'll avenge my master…"

In response, fierce iron arrows flew from all directions.

Qing swung the Five Poisons Sect's member's left arm.

His body swung along with it, and suddenly arrows sprouted everywhere.

"Hey, he's your disciple, you can't really shoot him…"

Beep! Beep, beep!

Qing's words were cut off by the sound of whistles from all directions.

Qing's expression suddenly became fierce.

\textit{Those damn whistles! Who's blowing the whistles!}

The whistles seemed to be a signal.

Bang! The sound of firecrackers exploding, and tiny objects scattered across a large area fly toward her.

They were a type of needle shotgun loaded with gunpowder. Qing immediately recognized what they were from the Hidden Weapons Armory that Tang Lan-Ah showed her in Sichuan.

Qing put the human shield in front of her.

At that moment, bang!

Shards of needles cover Qing's back. Ouch! Ouch, ouch, ouch!

"Ouch!"

Qing let out a cry that was not quite a scream.

That's because the pure power of the needle container isn't particularly strong unless it's fired directly at someone's face.

In the first place, the needle container opening was so large, so there were physical limitations to how much gunpowder can be loaded into it and still generated great power.

It's impossible to pierce the muscles of a martial artist like Hwa-kyung.

In fact, it couldn't even pierce the oil-stained ragged clothes that Qing was wearing.

However, some of them would scratch the skin, and a very small number would successfully stick into the skin like bee stings.

And in the first place, the power of the hidden weapons comes from the poison-soaked fragments, so it only needs to stick like a bee sting.

However, such a tiny poisoned needle had a very weak poison, so even if you use the most vicious poison, you have to hit your target from a distance to avoid danger.

This was why the poison dart was always used as a last resort, in close-range combat.

Were Five Poisons Sect, who were supposed to be experts in poison, unaware of even the most basic use of poison darts?

Of course not.

If a small amount of poison was not dangerous, they could simply add more until it becomes dangerous.

It was a foolish strategy that sacrificed the future of the Five Poisons Sect by using all of the sect's resources to completely soak the target in poison.

And the sect's resources included the lives of its members.

"How dare you! My precious skin!"

Qing, who had never cherished it in the first place, shouted angrily and tried to rush out again—

Suddenly, something wrapped around her leg and held her back.

When she looked down, despite his twisted left arm and being swung around, the meat shield was holding her ankle under his armpit.

When Qing's eyes met his, he let out a cackling laugh even as he spilled black blood filled with poison.

"Cough, wheeze, grunt, you can't go, you can't go…"

"Ugh! You filthy bastard!"

Qing was terrified.

\textit{This bastard, spitting blood everywhere, and rubbing my ankle on his armpit of all places—}

Meanwhile, ssshh, kang!

She tried to brush the hidden weapons away, but it kept flying at her, so he swas busy fighting it off.

"Shit, if you like my ankle so much, just keep it there."

Qing began to drag herself forward, even with the Five Poisons Sect clutching her ankle.

He was a very persistent man, dragged along the ground like a fish out of water, bouncing repeatedly, hitting rocks and tree stumps, yet clinging on like a leech.

However, it was said that the strength of the legs was three times that of the arms.

This meant that Qing, who was already unmatched in strength with her arms, could exert three times the force with her legs.

Qing ran!

With one guy hanging on her leg!

"There you are!"

These despicable guys seem to have decided to run away when she got close, then throw hidden weapons from a distance, and ran away again when she approached.

Qing's arm, with veins bulging on his forehead, draws a smooth arc, but stretches out powerfully.

Deeng…!

Suddenly, the sound of a Buddhist bell echoed through the tropical rainforest, like the fierce attack of a Buddha.

But it missed!

The intense force in the air bursts with a crackling sound, tearing the bark off the trees.

Qing was stunned.

\textit{No, how can that guy jump around like that?}

The movement of Five Poisons Sect's members  was mysterious.

Their running posture was straight, without any swaying, but they changed direction like lightning, moving in a zigzag pattern.

Thanks to that, they appeared and disappeared among the dense tropical forest trees. Just looking at it was mysterious and strange. What was that? Is it teleportation?

Normally, when a person ran sideways and changed direction abruptly, the upper body tilted and the legs extended outward to push off forcefully.

Therefore, the fact that they could change direction freely without changing their postures meant that their enemies could not predict their movements at all.

It was truly a mysterious and extraordinary skill.

It was no wonder that the Buddha's divine light missed its target.

\textit{Did Five Poisons Sect have such excellent Qinggong?}

\textit{It's really amazing, but why have I never heard of such excellent martial arts skills before?}

\textit{If I study Five Poisons Sect martial arts, will I be able to learn them too?}

Qing's eyes lit up.

Of course, it was Qing's misunderstanding.

Five Poisons Sect's members simply ran in a straight line, but because of the twisted illusion created by the formation, they looked moving left and right in an unpredictable manner.

The amazing technique mesmerized Qing.

Qing, who had just started learning martial arts, was momentarily distracted by the extremely powerful technique.

\textit{A sharp sound, unlike any other iron sound I've heard before. This is a javelin-}

The tips of Cheong's feet immediately rise up.

It is a joint that is extremely flexible due to the Ten-Star achievement of Flexing Flow.

Unbent left leg raised high above the head.

The meat shield that had been clinging to him until now also shot up, and-

Tung! The javelin that pierced the meat shield lightly struck Qing's steel chest plate.

"Guh!"

The meat shield spat out a mouthful of blood and met its tragic end.

The armpits, which had been clenched with all his strength, relax, and he fell from the high ankle he was holding.

As the meat shield, which had served its purpose, falls to the ground, Qing's figure was revealed.

She was covered in the blood that the meat shield had spilled.

"Ha…"

Qing wiped the blood-soaked blood from her face.