\chapter{Water Knows The Answer (4)}

Qing's expression immediately turned fierce.

This was because among those who played whistles at people, there were no normal individuals. They were all pieces of shits.

Above all, the memory of the Net of Heaven and Earth from Chen Changming's time was already etched as a scar in her ample bosom.

Soon, fishermen emerged from the cloth-covered fish farm's interior, each wielding weapons.

Qing drew her sword with a chilling gaze.

However, there were quite a lot of them.

They came pouring out like a disturbed beehive, to the point where it was hard to tell if this was a fish farm or a soldiers' barracks.

"Uh, that's quite a lot, huh?"

This wasn't said out of panic.

If it were, Qing's expression wouldn't have been so bright.

At a glance, they all seemed to be of similar cultivation, a bunch of easy targets.

For Qing, who was strong against the weak, it was just an opportunity to dance with her sword without burden.

"Ah. Ziyou! Friend, you stay out of this."

Even in this situation, Qing looked out for her weak friend.

From their conversation yesterday, Peng Chaolei was also a true martial artist who understood the true joy of being a virtuous, honorable expert.

If one had to classify it, it would be called the 'Pleasure of the Way'\footnote{A pun of 'Dao'. Dao can either means 'the way' as in Daoism, or the Chinese saber}.

After all, it would be a shame to miss the opportunity to play by looking after the weakling who tagged along.

Come to think of it, Tang Lan-ah's expression couldn't have been more accurate.

Indeed, it was insight worthy of a doctor of traditional medicine!

Ziyou tried to protest, but Old Dog quickly grabbed the Grand Prince and tucked him under his waist like a bundle.

"No, but…"

"Miss, to think you'd look out for the Young Master even in this situation. Please take care of your body."

Old Dog expressed his grateful thanks and swiftly retreated with the agility befitting a Master of the Unrestrained Realm.

Now with nothing else to worry about, Qing immediately took the lead, taking one step at a time to prepare to meet the enemy.

That's when it happened.

The enemies at the front simultaneously threw something, and pouch-like objects crossed the fence in succession.

As fire caught the yellow phosphorus inside the pouches and mixed with the contents, bright yellow smoke immediately billowed out, forming clouds.

The clouds flew straight towards them, riding the wind blowing from the riverbank.

"Wait, hey! Poison! Poison! Poison!"

Tang Lan-ah, right behind Qing, grabbed her wrist and made a fuss.

Qing smiled and answered.

"It's fine."

Black Heavenly Demonic Qi rushed out from the soles of Qing's feet.

Soon, Qing took a light step, Thud.

The ground vibrated, and Inner Qi vibrated with it.

While centered on Qing, in a wedge shape, it then went SWOOSH!

The surface of the earth flipped over, and soil and dry grass all shot up at once.

The poison clouds were torn apart left and right, flowing along the grain of their inner texture.

The first step of the Heavenly Demon's Reigning Step. Earth Qinggong.

When ten thousand demons advance, the Heavenly Demon takes the lead and steps forward, and even the earth reveres and raises itself to protect the ten thousand demons.

It was a legendary Divine Art that was said to be able to break tens of thousands of arrows with properties of the earth rising to a height of ten zhang.

Qing, who couldn't even handle Force, was merely imitating from memory, but with just that Qi Wave alone, she could easily split the smoke screen on the ground.

"W-What the?"

"Very good! Qing'er!"

A fisherman rushed in, but was dumbfounded by the clean air that centered solely around Qing.

One must remember that no matter how amazing a technique one encounters, one shouldn't be distracted during battle.

As Qing rushed past, she grabbed the fisherman's hair, and with that terrifying strength, his body was dragged in a straight line.

Qing advanced steadily, stepping with the Heavenly Demon's Reigning Step in the movement of the Yue Maiden Footwork. With it, her Inner Qi, too, slowly drained out.

However, there was nowhere else to use the Heaven-Shattering Demonic Qi.

Advancing without holding back, with each step, the ground flipped over, the earth swirled, and the poison fog was pushed aside left and right.

"Huh? What the? Where are you going? Why are you…?"

"Lan-ah! Come to your senses! Don't get separated!"

"Yes, yes! Sister!"

Tang Lan-ah suddenly came to her senses, and as her hands alternately went in and out of her bosom, she followed with sharp acupuncture needles between each finger.

Finally, a straight path was cleared through the pouches emitting poison fog to the crude fence about waist-high.

The Alleged Fishermen who had been about to jump into the poison fog in a line hesitated with their weapons raised at this spectacle.

Qing plunged into their midst and swung what she held in her left hand magnificently.

The fisherman whose hair she had grabbed drew a large circle, and his toes were embedded next to another fisherman's eye.

The battle between toes and eye socket was a loss for both.

The fisherman with the dented head was flung away, and at the same time, the caught fisherman's toe bones were shattered to pieces.

This was because the fisherman was wearing sandals woven from mere straw.

If he had been wearing safety shoes, only the head of the hit fisherman would have been broken, and the toes of this makeshift human weapon would have been fine.

Qing, reconfirming the importance of safety shoes, continued to swing the human weapon itself that she happened to be holding.

As it collided with enemies, foot bones and ankle bones were shattered, and when she thrust out the sword with that vicious momentum, the shins and knees were cut off by their comrade's very sword.

Every time she hit an enemy, screams burst out twofold.

Even when she missed an enemy, at least one scream burst out, so it was an excellent weapon that at least didn't disappoint the ears.

However, even that didn't last long.

Rip. With the exquisite sensation of tearing through flesh, the left hand she was swinging lost its weight and just swept through the air.

The human weapon she had grown fond of flew off somewhere, and only the whole scalp attached to the hair she had firmly grasped remained, dripping blood.

"Aw man."

Qing casually threw away the wig of actual human hair.

As expected, swinging by the hair isn't economical.

Just as Qing was clicking her tongue in disappointment…

"You witch!"

There was someone charging with a sword blade emanating purple Sword Threads.

However, compared to his realm, his swordsmanship was only Second-Rate, perhaps somewhere between White and Blue.

What's more, surprisingly, Qing was a swordsman!

She had already learned peerless swordsmanship, been trained through duels with Ximen Surin, and even seen the Celestial Martial Emperor's Sword Style, so her discernment was already that of a true master.

Qing scattered the clumsy illusions contained in the swift sword and extended her Moonlight Sword (No. 8) in a straight line towards the enemy's heart.

It was a move that Ximen Surin would have praised as a perfect counterattack if she had seen it.

However, the opponent was also in the Late Stage Peak Realm, so he wasn't easy to deal with; he twisted his body at the last moment, narrowly avoiding his heart and ending up being pierced from his ribs to his back.

Then came a woman's scream, like breaking glass.

"No! Gege\footnote{'Brother', but only used by couple}!"

"Junior Sister! This witch! We need to move quickly!"

The Peak Realm fisherman shouted while firmly grasping the thin blade of the Moonlight Sword with both hands.

Qing tried to pull out the blade, but with the bones of his hands protected by a Protective Mirror and interlocked with both hands, thus leaving only the fisherman's body to keep shaking.

It was the mindset of dying together.

Qing frowned.

She could just let go of the sword, but then she'd be letting go of a Late Stage Peak Realm enemy, which she didn't want to do.

Besides, it somehow felt like losing.

Qing raised her right arm high.

It was the principle that people used the ground to support their strength; when lifted up, they couldn't possibly resist.

The Late Stage Peak Realm fisherman was lifted up, thus skewered on the sword.

Then the slender fisherman running behind him was revealed, and Qing saw her eyes widen.

"Let go of my Gege!"

Qing answered.

"As you command!"

Qing swung her right arm down with all her might vertically.

The man skewered on the sword stood on the ground with both feet.

Following the law of inertia, only Qing's blade slipped out from between his legs.

The Late Stage Peak Realm master who had become a human embodiment of the 人 shape sprawled on the ground.

As his head drooped, it looked more like the character for 'enter' 入 than 'human' 人.

"Gege! Gege!"

The woman grabbed and shook her man's corpse, ignoring the great enemy in front of her.

Thanks to this, the diligently gathered hands came loose and were in danger of changing to something resembling the character for 'big' 大.

\textit{Were they perhaps lovers?}

\textit{A pair whose combined Evil Karma exceeded six hundred.}

\textit{Rather than being united in marriage, it would be better for the world if they stabbed each other and went to the afterlife together. Yet here they were, acting out a melodrama.
}
Remember, the thing Qing hated most in the world was racial discrimination. The second was Chinese, the third was blackies, next were European imperialists, and finally, in fifth place was excessive melodrama.

Having satisfied two of the five things she hated most in the world, the verdict was naturally death.

Just as Qing was about to enjoy the solid impact of the Black Slaying Demonic Palm for the first time in a long while…

"Junior Brother! You wench! I'll tear your crotch apart!"

A middle-aged fisherman leaped in with an ominous Qi Wave.

\textit{Shit, what the hell. A Transcendent?}

Qing took a slight step back.

Of course, she didn't forget to run her mouth.

"Tear my crotch apart, you say. Your words are too harsh. To abbreviate, let's go with YWH. If both are abbreviated, it's 'CT? YWH'. Did you know that young people these days all talk like this?"

"You wench!"

The middle-aged fisherman's face turned bright red.

"Besides, your junior just died with his crotch torn apart like that. Is that really what you should be saying in front of the grieving widow?"

"I'll kill you!"

The middle-aged fisherman's sword began to emit light on its own.

Sword Force. The starlight destruction allowed to those in the Transcendent Realm.

At that moment, Qing launched her body.

She touched the ground, rolled twice, and charged low, grabbing the ankle of the Junior Sister fisherman who was kneeling.

"Junior Sister whose name I don't know! Since your Senior Brother is cowardly attacking a Peak Realm, I'll borrow your strength for a bit!"

Qing swung her arm in circles above her head.

The Junior Sister fisherman rotated at the same speed.

"W-What are you doing!"

"Pop quiz! Your Junior Sister is rotating at one revolution per second! Her weight is about 80 catties! Her height is about 5.5 chi! Calculate the sister at this moment!"

Qing charged while swinging the Junior Sister fisherman.

The Transcendent fisherman recoiled greatly, too afraid to even attempt swinging his sword surrounded by Sword Force in actual combat despite reaching the Transcendent Realm; he was busy just backing away.

"Junior Sister, I'm counting on you!"

Qing staggered and put great force into it, and the Junior Sister fisherman shot out like an arrow in a straight line.

Qing followed right behind, raising her sword.

The Transcendent fisherman's choice was self-preservation over his Junior Sister.

He leaped high, launching his body into the air, and the fiercely flying Junior Sister fisherman collided with the ground, making a long red line as she landed violently.

Qing didn't miss the opportunity and shouted as she charged!

"You didn't catch her! Murderer! You killed her! Your own Junior Sister! And you dare call yourself a Senior Brother?!"

Qing reached out her hand while spouting nonsense.

DING-! The sound of a temple bell!

He never imagined she would use an Air Palm, so the Transcendent fisherman who had carelessly lifted his body into the air had no way to avoid it.

Qing quickly ran to the fallen Transcendent fisherman.

"P-Please spare…"

Qing looked at the Transcendent fisherman's Evil Karma.

If his Evil Karma had been just 200 points lower, she would have spared him.

\textit{What a shame.}

"The Junior Sister you killed probably wanted to live too."

Qing stomped on the Transcendent fisherman's neck.

Qing's footprint was deeply engraved on the earth, and compressed meat remained in the shape of the sole of Qing's leather shoe.

It was a historic moment for the Transcendent fisherman's neck, as it was liberated from his body, but sadly, it was caught by Qing's hand immediately.

Qing raised the Transcendent fisherman's severed head high.

"Enemy general! Defeated!"