\chapter{Water Knows The Answer (3)}

The greatest architectural achievement in Chinese history.

This referred to the Dujiangyan.

Built around 250 BC, this structure literally cut through a mountain to create a waterway.

One must think; in those ancient times, what tools could they have had?

Using only the primitive method of heating rock faces with furnaces and then breaking them, they ultimately created a new river that didn't exist in nature.

The farmland created this way was equivalent to 25,000 sports stadiums by the standards of Qing's homeland.

The land of Sichuan, which was originally a humid, hot, and dense jungle, was transformed into prime land capable of nurturing all under heaven.

Qing listened to this proud explanation with one ear and let it out the other.

It all depended on one's background, after all.

In her homeland, they were already experts at controlling waterways.

\textit{What's so great about just dividing a waterway and building some embankments that they have to make such a fuss?}

\textit{What was more impressive was the cooking of the Greatest Chef Under Heaven.}

The taste was as excellent as the chef's conviction.

In other words, she ate an enormous amount.

Thanks to that, after eating, drowsiness was washing over her, and she just wanted to take a nap.

\textit{Why make such a fuss over a few foreign fish species entering the water?}

As she arrived at Dujiangyan while nodding off like this, what she saw was just an impressive waterside.

Places with stakes driven in, nets connected, and tents pitched above were all fish farms.

The aquaculture technology of primitive ancient uncivilized China was just about this level - the mere act of confining fish and feeding them was considered farming.

The group began checking each farm, starting from the closest one.

"Please, o' Master. This stake was driven in by my grandfather, and my father and I have managed it to grow it to this point."

"So, where's your permit?"

Tang Lan-ah shot back confidently, then glanced at Peng Chaolei.

It was a mysterious phenomenon where both her rudeness and politeness increased simultaneously when Peng Chaolei was in sight.

"Well, about that…"

The fisherman trailed off.

That's right.

Even in Qing's homeland, a world where the rule of law had been established through legislation, wasn't it the same?

Every valley was full of less-than-human parasitic vermin who had lost their conscience, laying out platforms and overcharging while claiming baseless ownership.

If the descendants of the great Hwanguk were like this, how much more so would the uncivilized Chinese people be?

The basic sentiment of Zhongyuan people was that anything was fine as long as you didn't get caught.

This had been passed down from ancestors to descendants, continuing into the future as the most fundamental way of thinking of the Chinese people.

So, a permit for a fish farm?

Only fools and idiots would get such a thing.

"No, you lowly… I mean, look here, shouldn't you inform our Tang Clan about these things and request protection? How will you receive protection if something happens?"

It was a demand for protection fees if they wanted to do business.

This was the way of Wulin.

Why would they learn martial arts just to farm?

A better and easier method was to take from those who farm.

Because it was an easier and better method, everyone strived to learn martial arts.

Of course, there was no need to curse Wulin practitioners.

This was the way of humanity; the history of people was that those who have exploit those who don't.

Whether it's through fists, systems, or the power of wealth.

The fisherman's face fell.

"It's… it's not that profitable a business."

"Is that so? Well, then there's nothing we can do. I wonder if other fish farms want protection or not…"

Only then did the fisherman realize he had no other choice.

If other fish farms caused trouble and they were backed by the Tang Clan's influence, he would have to give in without resistance.

If he resisted unnecessarily, the Tang Clan's martial artists would come in force.

After all, the Tang Clan was a righteous prestigious orthodox sect that properly delivered on the protection fees they received.

Since he hadn't reported to the government office, it was obvious the authorities wouldn't get involved.

"I'll take it! Of course, I should request protection from the Tang Clan's experts!"

"Good. When a Tang Clan warrior visits later, settle the account and receive a flag. Until then, you can say the Speaking Poison Flower guaranteed it."

Qing watched this scene and thought:

\textit{Wow, she's good at business.}

\textit{She is different from Crutch after all.}

\textit{Maybe it's because I saw her tending to patients this morning, but she seems somewhat smart.}

\textit{Despite her appearance, she's actually a proper doctor of traditional medicine!}

Only Ziyou looked uncomfortable.

And Ziyou, being a Grand Prince, didn't particularly hide his discomfort.

"I see. Private groups profit even though the government is right there."

At this lament, Qing burst into laughter.

"Have you ever seen the government actually work? What's the difference?"

From Qing's objective numerical observations, the Evil Karma of those affiliated with government offices was much higher than that of Wulin Practitioners.

This was probably because Orthodox Wulin Practitioners actually caught thieves and gangsters to match the protection fees they received. And incidentally, they quickly beat up manageable Demonic Adepts when they appeared.

In fact, Orthodox Wulin was essentially maintaining law and order in Zhongyuan.

Wasn't this the case? For reference, look no further than a recent memory of her drifting on a boat.

It wasn't even a government official, but the son of an official who was tyrannical.

At this, Ziyou tightly closed his mouth.

Qing grinned.

"See? Isn't it kinda embarrassing even though you're the one to say it?"

"…Not all officials are corrupt."

"Sichuan seems pretty okay. Just Sichuan, though."

The group, or more precisely, the precious daughter of the Sichuan Tang Clan, conquered the fish farms one by one.

Even in this situation, Qing didn't pity the fishermen.

Because Qing, now a proper martial artist with 4 years of experience in Zhongyuan, knew how the world worked.

They cowered because they recognized Wulin practitioners and the Speaking Poison Flower, but if there had been someone who didn't recognize them, they would have immediately charged at them with bamboo spears.

The fishermen were not innocent fish farm owners, but illegal street vendors.

At this point, they were almost at the end of the left bank.

In fact, the higher up they went, the worse the location became, because the feed used for farming flowed downstream.

So while the prosperity should have gradually decreased as they went up, this fish farm had stakes extending far out with several planks reaching far into the distance.

A fisherman who had been handling nets on the other side began to approach with quick steps as soon as he saw Qing's group.

"Eh?"

While Qing frowned, the triumphant Tang Lan-ah stepped forward again.

She had become more and more triumphant with each tent, and now she practically had the air of a feudal lord, unparalleled in arrogance under the heavens.

"Hey, Mr. Fisherman. Who gave you permission to farm here?"

"Well about that… I apologize, but this is a business approved by the Councilor."

"I thought as mu- Huh? Wait, what did you say?"

"Since this is a business site approved by the Councilor, if it's perhaps something the Lord knows about…"

The fisherman spoke while shrinking his neck and looking cautious.

"Ah. That fat pi- I mean, that person. I was wondering where he kept finding new sources of money."

Tang Lan-ah frowned.

The Councilor was essentially the right hand of the Sichuan Provincial Administration Commissioner.

The Sichuan Provincial Administration Commissioner was the final authority for provincial affairs in Sichuan, excluding military matters (in modern terms: the Governor), so the Councilor was the second-in-command among Sichuan's public officials.

With the establishment of the royal prefecture, the ranks of officials including the Provincial Administration Commissioner had been pushed down about three steps, though.

"If I need to show you the permit…"

"No, that's fine."

There was no need to unnecessarily antagonize the Councilor.

Just as Tang Lan-ah was about to back off…

Qing, who had somehow come up beside her, chided her.

"Young Lady Tang. Didn't we come all the way here for something other than collecting fees?"

Somehow, the Ouyangji had become an afterthought, and she was solely focused on selling flags.

Tang Lan-ah's earlobes turned red.

"Right. I mean, no. I-I knew that, okay? Look here. Forget about the protection fee, can we take a look inside? It seems like someone is raising Ouyangji in large numbers."

"Ouyangji, you say? Who would!"

Right as he was saying ‘Who', the fisherman stretched out his hand.

A beam of sharp light with a long tail rushed towards Tang Lan-ah's face.

And one delicate hand blocked its path.

Qing, who had been slowly approaching and taking position because the fisherman's Evil Karma seemed unusual, had stretched out her hand.

Something slipped between her index and middle fingers.

Checking, she found she had caught a dart.

Qing, who had inadvertently caught the dart with two fingers, exclaimed in admiration.

"Oooh. That was kinda cool of me, yeah?"

"Tch, CHARGHK!"

He probably meant to shout "CHARGE!", but…

Because a dart was deeply embedded in his shoulder, it ended in a scream.

Qing struck the fisherman's dantian.

As he doubled over with an Oof, she grabbed his neck and punctured a hole under his vocal cords with her thumb.

At the same time, she grabbed his uninjured arm and rotated it greatly towards his back.

Pop, the sensation of the shoulder joint dislocating.

The feeling of liberation, as if something loose had come out in one go, was exquisite.

Riding the momentum, she rotated it further, and with a tearing sound, she felt the tendons ripping like a fish nibbling on bait.

Qing smiled brightly as she pinned the man to the ground and firmly stepped on the middle of his back.

As his spine crumbled, the man's lower body, which had been thrashing, immediately stopped moving and went limp.

Because a hole had been punctured under his vocal cords, he couldn't even scream, and only the loud sound of rough breathing could be heard.

\textit{Ah! This is the shit.}

\textit{As I thought, destroying bad guys is the best.}

The Zhongyuan people's mindset of 'It's fine as long as you don't get caught' differed from other races in that it wasn't 'It's okay if you do it secretly' but rather 'It's okay if you eliminate all witnesses.'

They were the type to kill everyone to silence them if things went wrong, so judging by this Evil Karma, he must have buried quite a few people.

"Young Lady Tang, are you okay? You seem very shocked."

"Ah, ah. Yes…"

Tang Lan-ah, who had been frozen in a daze, finally focused.

"H-Hmph! I could have handled it perfectly well without your help, you know?"

"Sure. But catching that dart was pretty cool, right?"

"That was a little… No, I mean. It wasn't cool at all! And that's not a dart, it's a throwing blade!"

Tang Lan-ah shouted after inadvertently agreeing.

"Yeah, yeah. Whatever you say."

"What! It's not just 'Whatever you say'."

"Hm? Looks like this guy's about to die."

Qing spoke as if looking at an insect.

"I didn't give him any fatal wounds, though? Did I utilize too much of my previous experiences into that stomp?"

As Qing flipped him over with her toe, he was rolling his eyes with black blood trickling from his mouth.

Tang Lan-ah quickly grabbed Qing's wrist and pulled her towards herself.

"Step back. It's poison, poison."

Then she swiftly cut the clothing around the throwing blade embedded in the patient's shoulder with the tip of a knife.

Black blood, killed by the Poison Qi, gushed out.

It was at the moment that Tang Lan-ah's expression hardened at the unusual details.

SCREECH!

A violent sound of a whistle rang out.