\chapter{Water Knows The Answer (2)}

The news that the water had gone bad was not something to be taken lightly.

Water was essentially life itself.

In the primitive ancient uncivilized Zhongyuan that depended on agriculture, the importance of water could not be overstated even with hundreds of asterisks.

In the past, King Yu manipulated the floods and established the domain of Zhongyuan, stabilizing the world through water management.

This moved Emperor Shun so much that he passed the throne to Yu.

The Three Sovereigns were gods, and the Five Emperors were demigods. Emperor Shun, as the last of these Five Emperors, passed the throne to humans.

It was a historic moment when the Emperor transitioned from a mythical being to a human.

In other words, the link between myth and humanity laid in water management, the control of water.

This was how important water was.

"What do you mean the water has gone bad?"

"I am not sure. We always use well water from the upper Min River because it's good, but it's the same with all the wells I visited throughout the night. However, the taste of the water from the Tuo River is still fine, so I think there might be a problem with the Min River. Isn't this kind of thing the specialty of the Tang Clan's experts?"

Sichuan has two waterways flowing east and west.

They were called the Tuo River and the Min River as they flowed to join the Yangtze River.

They were also called Tuo and Min without the 'River' part.

Several streams flowed through Chengdu city, but the main waterways were four rivers branching off from the Min River.

Starting the Yunyang River flowing north, in order, the Baidu River, Zhuma River, and Dao River were known for their clean and clear water taste, often used as a basis for Sichuan cuisine to claim it was the best in Zhongyuan.

It wasn't just about the taste of water.

Most rivers in Zhongyuan were yellow, murky, and tasted of earth.

Rivers clean enough to drink directly were common only in Sichuan, rare in other regions.

"The Min River is always busy with boats, so isn't that why? But it's not something we can easily dismiss. Let's go to the Tang Clan first."

Ziyou naturally tried to lead the group.

Tried to, that is.

Qing took a step back.

Her stomach was too upset to be swept along by such an atmosphere.

It was because she didn't know whether this river or water management issue was serious or not.

"I need to eat lunch. It's breakfast and lunch combined, so I can't delay any longer. You go ahead first. I'll eat with Gramps and come in later, okay?"

However, Ziyou was starting to understand how to handle Qing.

"No, with the Greatest Chef Under Heaven here, why look for another chef? You must have wanted to stand in the Tang Clan's kitchen at least once, haven't you?"

At this, Bai Changzi took offense.

"I've already refused the Tang Clan's offer. The place I wanted to stand was not the Tang Clan's kitchen, but the royal prefecture's kitchen."

He was saying this in front of the very Prince of that royal prefecture, so it was like being blind with eyes wide open.

It was frustrating, but also admirable in a way, leaving Ziyou at a loss.

Qing let out a hissing laugh.

"Friend, you lack the finishing touches, it seems. Hey, Mister Chef. Is help just one-way street? Are you saying you can't make a meal for us?"

As Qing reached out her hand, Cui Liweng appeared from somewhere and placed a magical flute in her hand.

Then Bai Changzi spoke proudly.

"Haha. As a chef of Sichuan, shouldn't I stand in the Tang Clan's kitchen at least once? I'm extremely curious about what kind of ingredients they might have."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Tang Clan occupied an entire neighborhood district called Tang Center, where only members of the Tang Clan lived.

As they entered Tang Center, the second? third? fourth? direct descendant of the Tang Clan appeared from somewhere.

\textit{Was he the one with the tail? Or the neck meat? Or the Jian Nan Chun?}

Qing wasn't sure because she hadn't paid much attention.

But a few more of those brothers appeared afterward, so whether it was the second or third, it seemed like someone would be there if called.

Anyway, after explaining the situation, Tang So-And-So nodded.

"If that's the case, we should call our Ah'er. She should be tending to patients at the Tang Clan Clinic right now."

"Her?"

Qing recalled the rather dubious Tang Lan-ah.

Though her face looked fierce, there was something about her that reminded Qing of Senior Sister Wannabe, making her an unreliable choice.

"There's no Poison Master in the Tang Clan who can handle poisons as freely as Ah'er. I'm not saying this because she's my sister, but it's truly a heaven-sent talent."

Tang Lan-ah always carried custom-made Combination Poisons.

They were all terrifying poisons that targeted only the face of the opponent.

They were actually deadly poisons that were difficult to detoxify, taking effect after just a few breaths.

To the clan's Poison Masters, it was heartbreaking that this heaven-sent talent was used to create poisons that merely caused consecutive sneezing or unnoticeable tears.

Nevertheless, Tang Lan-ah was one of the Tang Clan's top Poison Masters.

The 'poison' in Speaking Poison Flower title wasn't just given because the child was vicious, insidious, and ill-tempered.

Of course, there was also the fact that the Tang Clan no longer focused on poisons, so the Poison Masters were just analyzing what was available and not at a high level.

The Tang Clan now focused on a different area.

"Wow. Clinic…"

Qing marveled at the sight of the massive Tang Clan Clinic.

The seven wide-open gates revealed a vast courtyard where patients lined up.

Physicians sat in rows in the converted main hall, examining patients with solemn expressions.

The savory smell of medicinal herbs being decocted whetted one's appetite from afar.

"These are the Seven Great Gates of the Tang Clan Clinic. Anyone who is sick can freely come and go, so even in the dead of night, at least two gates are always open. This is also why there are no other clinics in Chengdu."

"Oooh."

The Tang Clan now focused on medicine.

Since there had been no enemies in Chengdu since the time of the Celestial Martial Emperor, the Tang Clan's poisonous heart had softened.

Thus, they opened the doors of the Tang Clan Clinic wide and cared for patients for free, even taking a loss on each pulse diagnosis.

However, it wasn't charity.

Medicine was originally an accumulation of empirical experiences.

The accumulation of countless cases led to an explosive development in the Tang Clan's medical knowledge.

Qing nodded at the mention of unlimited free treatment.

No wonder the Righteous Karma of the Tang Clan people wasn't low.

When Tang Lan-ah pushed aside reservations, people grumbled but didn't curse her because of the goodwill they had built up usually.

Ziyou smiled bitterly.

This was also why the Grand Prince didn't bother to crush these parasites who were gradually nibbling away at his assets.

Even if they acted a bit arrogantly and tyrannically, they rarely harmed people, and instead saved lives with their medical skills.

Unless it was at the level of embezzling mines or treasonous gunpowder manufacturing, he could turn a blind eye.

It could even be said that they were more beneficial than Daoist sects that only ate without producing anything.

In one corner of the Tang Clan Clinic, they found Tang Lan-ah, who was tending to women. She opened her eyes fiercely and said:

"Ha, what is it? Do you think Lan-ah is someone with nothing to do who will do whatever you ask and look at whatever you want her to see? And Elder Brothers should know better too. Falling head over heels for that unworthy one and throwing away their pretty little sister. Hmph."

\textit{Ah. They did say she had a nasty temper, huh.}

\textit{Yeah, I did think she was unexpectedly docile for someone said to have a nasty temper.}

This was the Tang Lan-ah without Peng Chaolei next to her.

"Look here. It's not about any little thing, but a matter of water management. Personal feelings shouldn't…"

"What are you saying? The weakling who tagged along seems to have a mouth that is used far too much."

Then she dipped into the water they brought, tasted it, tilted her head side to side several times, and finally took a big gulp and drank it all down.

"There's nothing wrong with it? Making a fuss over nothing. Ridiculous. Everyone get out! Lan-ah is going to see patients."

Because her face was pretty, even when she referred to herself by name, it didn't trigger the urge to give her a nuclear noogie.

If it had been Crutch or Chen Changming, they probably would have deserved a nuclear noogie.

Anyway, she didn't seem willing to help, and it felt wrong to hold back a physician who said she was going to tend to patients.

That's when it happened.

"Hmm. Where is Lan-ah… Oh. Qing'er. With something covering your face, I can see you even from afar."

It was Peng Chaolei, who had come to the Tang Clan Clinic after hearing that they had prepared Shiquan Teapills4 that she had personally brewed.

"Ah. Hello. Good morning, isn't it?"

"Morning? Qing'er, a martial artist should be diligent. The sun is already high in the sky, so you shouldn't say such things. A proper martial artist should wake up when dawn is still screaming and sweat through training."

"Sister!"

Peng Chaolei, who didn't seem like she would do such a thing, suddenly started nagging.

Fortunately, Tang Lan-ah interrupted the nagging by rushing out and hugging the nagger's arm.

"Hehe, Sister, you came?"

"Oh my. Were you in the middle of tending to patients? I didn't see you that way, but you have an admirable side? That's good. That's really good."

"Hehe. It's nothing. …Wait, huh?"

\textit{What's this? Something's strange. Is this supposed to be praise?}

While Tang Lan-ah was slightly confused…

"But I feel left out. Are you all gathering without me? Qing'er, is there something fun going on?"

"The only fun thing is that the Greatest Chef Under Heaven here is going to make us lunch. Other than that, there's an unfun thing. They say the water has gone bad."

At this, Peng Chaolei's face became as serious as if something had gone bad within her too.

Everyone except Qing knew it was a serious problem.

"That is indeed a serious problem. Ah. So that's why Lan-ah was trying to check?"

"Of course! Who else in the world but me would volunteer for such a serious matter!"

As she said this, she shot a venomous glare that seemed to say 'Don't you dare speak'.

Qing and Ziyou thought as they watched this scene.

'Isn't she like a dog?'

'For some reason, she looks just like a dog.'

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Something did come out.

Even Tang Lan-ah looked surprised.

"There's a fish called Ouyangji\footnote{歐陽鯽, lit. 'Ouyang carp'. Oyangjeuk (오양즉) in the original text. 'Ouyang' might refers to Ouyang Feng, a character from Jin Yong's novel 'Legend of the Condor Heroes', nicknamed the Western Venom. Ouyang itself means 'south of Mount Ouyu' (currently Mount Sheng, Zhejiang)}that carries poison. If it spreads in large numbers, it could dissolve in the water to some extent. But it's not particularly harmful to the body. Unless you get stung by a Hongtousuanglifeng\footnote{紅頭雙黎蜂; lit. 'red-head black-pair bee'. Hongdusangyeobong (홍두쌍려봉) in the original text} after eating it. But anyway, they only live in Yunnan, so there's no need to be careful in Sichuan."

"Ah! That's right! I thought the taste was familiar, it was the fishy taste of Ouyangji! Eut?"

Bai Changzi interrupted Tang Lan-ah's words and shouted, then suddenly grabbed the back of his neck.

He seemed to pull out a thin needle, and then his nose turned bright red and started gushing mucus.

"How dare a mere chef interrupt someone's words. Hmph."

Tang Lan-ah looked at Bai Changzi with a sour expression.

"By the way, is he even human? How does he notice a change in water taste just because some river fish have changed?"

"Ish true. I am the Greatesht Chef Under Heaven, sho of courshe I would notishe. Thish ish the pride of the Greatesht Chef Under Heaven. Sho, what should we do now? Are we jusht going to leave it like thish?"

Bai Changzi asked, undeterred by his runny nose.

In a way, he was a very consistent person.

"Anyway, Ouyangji can't survive the winter, so they'll all disappear after this winter. But, it is a bit strange."

Tang Lan-ah furrowed her beautiful brow.

"Ouyangji is a fish that only lives in Yunnan, so it doesn't suit Sichuan at all. The water doesn't match from the start. But you're saying it has reproduced enough for the poison to dissolve in the water?"

"It'sh shtrange. There hasn't been any increashe in Ouyangji at the market."

It was a way of thinking that only a chef would utilize.

If Ouyangji had reproduced, wouldn't fishermen have immediately caught them and put them out in the market?

"Then, is someone trying to farm them? If the whole Min River is like this, it must be upstream at Dujiangyan. What? Someone set up a fish farm at Dujiangyan without the Tang Clan's permission? How dare they."

Ziyou frowned.

To set up a fish farm at Dujiangyan, one should report to the government office and get permission from the rightful owner, the royal prefecture. Why would they need the Tang Clan's permission?

"Anyway, we'll know if we check directly, right? I was bored, so this is perfect timing."

Peng Chaolei grinned as she summarized the situation.

Qing added one more thing.

"Let's eat lunch first."