\chapter{Water Knows The Answer (5)}

Peng Chaolei's dadao moved erratically.

The fishermen's True Qi was mixed with an ominous purple color.

Purple True Qi was a typical characteristic of Poison Qi.

After all, in reality, how many purple-colored poisons could there be? But since True Qi was originally based on Imagery, it was unavoidable.

When people think of poison, they imagine purple, so the True Qi of Poison Arts followed that Imagery.

Opponents with Poison Arts were extremely troublesome.

Even a small scratch could lead to fatal poisoning, so one naturally became protective of their body, unable to maintain an offense and being pushed into a defensive position.

"Sister, it's dangerous!"

With a cute Ping Ping sound, something round flew past Peng Chaolei.

However, the result was not cute at all; the opponent who was hit by the curved hidden weapon immediately burst into tears, staggering as they couldn't see.

The Tang Clan's Petal Lotus, an irregularly shaped lotus-like hidden weapon, was infamous for its disorienting sound and confusing trajectory.

It was not easy to handle, showing that Tang Lan-ah's achievements as a martial artist were by no means low.

Peng Chaolei didn't miss the opportunity and swung her dadao imbued with Force, causing the fisherman to be horizontally split and roll away.

Then, turning her body fluidly, the dadao flowed and cut another fisherman's waist in half, settling behind Peng Chaolei's back.

It was the preparation movement for the famous Five Tigers Breaking the Gate Dao.

To be more specific, it was a family martial art of the Peng Clan that pursued extreme speed with a massive dadao. When mastered, the rapidly striking dadao was said to have the momentum of five tigers.

By using a heavy weapon to achieve extreme speed, it was a peerless dao technique that possessed both weight and speed simultaneously.

One swing of the dao could split a person in half, so the surprised fishermen hesitated and widened the distance. Then, they started throwing hidden weapons.

Peng Chaolei's dadao drew dense lines, creating a net-like shape.

This artful technique was called a Curtain.

If done with a sword, it would be a Sword Curtain, but in this case, it was done with a dao, so it would be called a Dao Curtain.

With clashing sounds, the heavy hidden weapons were deflected by the dao, while the lighter ones were swept away by the wind generated by the dadao.

The fishermen got excited at this and threw more hidden weapons.

The Curtain originally consumed a lot of stamina and Inner Qi, so it couldn't be maintained indefinitely. As such, they thought to pour hidden weapons at this time.

However, showing off hidden weapons in front of the Sichuan Tang Clan was futile.

Tang Lan-ah pulled out a large bamboo tube from her bosom.

For reference, it was characteristic of Tang Clan members to keep pulling things out of their bosoms.

And the reason why the Tang Clan was feared was precisely because of what was in those bosoms.

The fishermen's faces turned pale.

"Rainstorm of Pear Blossom Needles! Scatter!"

Someone shouted a warning, but it was too late.

BOOM!!! The sound of explosives.

Thousands of thin needles poured out towards the front.

Each was a fine needle coated with dried poison.

As the needles penetrated the body, the powdered poison dissolved upon contact with blood, causing people to foam at the mouth and collapse shortly after.

Peng Chaolei took a breather and looked at Qing.

Since Qing had quickly advanced ahead with the old man, the two of them ended up taking charge of the rear, so she wanted to quickly check during this brief lull.

"Ha. My goodness…"

At that time, Qing was in the middle of grabbing a fisherman's foot and spinning him around as a threat.

Peng Chaolei's eyes shone.

\textit{That is the true strength of the flesh!}

Finally, Qing staggered greatly and threw what she was holding. Then, simultaneously, DING-!

The sound of a Buddhist temple bell rang out, causing everyone to look towards the source with surprised eyes.

-Enemy general! Defeated!

The round thing held up high was probably a head.

Peng Chaolei thought that perhaps Qing enjoyed reading the Romance of the Three Kingdoms. However, that wasn't the important thing at the moment. Dealing with the fishermen took priority.

"Most Senior Brother!"

Some cried out in anguish, while others lost their fighting spirit and pulled back their hips.

At that moment, Qing's voice rang out again.

-Those who surrender will die comfortably, those who run away will be chased to the end! Those who want to live will die, and those who want to die will also die!

It was a threat never heard before in the world.

Wasn't she saying she would kill them no matter what?

Even a lowly field mouse would bite an ankle in desperation if cornered, so wouldn't this rather provoke the enemies?

However, before Peng Chaolei could lament, the enemies scattered and ran away.

Peng Chaolei marveled.

Since they were going to die anyway, was this a decision to scatter so at least one might survive?

\textit{Perhaps Qing'er's strategy…}

In the midst of this, her voice rang out again.

-Where are you going! You fuckers, consider yourselves dead!

Peng Chaolei thought again.

\textit{It is a strategy… right?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There were cases where one won the battle but lost the war.

And this was precisely such a case.

"Ah. The Ouyangji…"

The fish farm was empty.

After the nets on the stakes were cut, all the Ouyangji in the vast fish farm had gone into the Min River.

Still, it wasn't a complete loss.

At least they had found out the identity of the fishermen.

"Yunnan Poison Man, Ci Zhezhu\footnote{慈哲朱. Ja Cheolju (자철주) in the oroginal text}. The Most Senior Disciple of the Five Poison Sect."

Qing tilted her head.

\textit{How can his nickname be Yunnan Poison Man?}

\textit{Then is the Tang Clan's most Senior Brother's alias Sichuan Poison Heaven?}

\textit{Or maybe the Tang Clan, being a noble clan, doesn't have a Most Senior Brother?}

\textit{Come to think of it, Sichuan Poison Heaven sounds kind of cool.}

"But how did you win? Ci Zhezhu's realm should be at the Late Stage Transcendent, right? You're only at the Late Stage Peak Realm, aren't you? How did you win?"

"He didn't seem that strong, though? Compared to the Demonic Cannibal, there was a huge difference."

Of course, Qing was already in a state incomparable to that time.

Not only her Inner Qi but all her physical abilities had surpassed human limits.

However, there was a more fundamental reason.

"Our Qing'er had good luck. It seems he couldn't use his poison out of concern for the woman Qing was grabbing and swinging around."

The Poison Dan that Poison Art practitioners possessed was a form where poison was concentrated in the center of the dantian and wrapped with Inner Qi.

The more skilled the Poison Art Master, the more vicious the Poison Qi in the Poison Dan becomes, so if it was not well-protected by Inner Qi and leaked out, it could harm its owner.

As a result, if you exclude Poison Arts from a Poison Art master, they were at the level of a half-cripple compared to others of the same realm.

Protecting the Poison Dan limited the usable Inner Qi, and the speed and power of its operation also fell far behind due to the constant attention required.

That's not all.

Gathering a Poison Dan was a process of studying all kinds of poisons, absorbing them into the body, and nurturing them.

Naturally, they had less time to train with weapons, so they were also half-baked in terms of pure skill.

If their dantian was damaged during a fight, they could die from being poisoned by their own poison.

"Ugh, Sister. If you say it like that…"

Tang Lan-ah couldn't hide her disappointed expression.

Saying it like that made Poison Arts sound like trash, after all.

"Of course, that's only if you exclude the poison. Since poison doesn't distinguish between allies and enemies, he was stupidly defeated by a single hostage. But originally, they are quite tricky to deal with."

True Qi mixed with Poison Qi would seep in a little poison just by clashing or grazing.

And that's not all.

They quietly released poison and pushed it in using the principle of Material Void Absorption, or carried around outlandish hidden weapons, or spit poison or sprinkle blood - the risk of poisoning was so high that it was even tricky to engage in direct combat.

However, Qing, who didn't have to worry about poisoning, roughly concluded.

\textit{So, people who handle poison are easy targets.}

\textit{Then the Sichuan Tang Clan isn't all that either.}

As Qing was thinking this…

Peng Chaolei looked at Qing with a subtle expression.

"By the way, Qing'er?"

"Yes?"

"I saw you fighting, and, ahem. I don't mean anything by it, so please don't be offended, but can you listen?"

"What is it?"

However, Peng Chaolei spoke with a serious expression.

"Qing'er. A dao suits you better than a sword."

"Oing? Me? I do?"

Peng Chaolei answered with a voice full of conviction.

"Yes, and a very large dao at that."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{Life as a guest was truly paradise.}

\textit{If only Senior Sister Wannabe were here, it would be perfect.}

\textit{Then I could have her help me bathe, do laundry, and dress me every morning…}

Suddenly, a thought occurred.

\textit{Haven't I become a bit of a degenerate lately?}

\textit{I'm sure that right before I went to the Demonic Cult, I was happily dancing with swords with my Sword Friend.}

\textit{Surely, the Ximen Qing of that time had a soul that sparkled with desire to become a master.}

\textit{How have I become so depraved?}

\textit{Come to think of it, it's all because of those Crutches.}

\textit{Not walking with my own feet, not washing with my own hands, not dressing myself - I've completely let my discipline go.}

\textit{Thinking back on it, it was all the evil scheme of those Demonic Cult bastards.}

\textit{When did I start finding sweating unpleasant?}

Qing reflected deeply and thought.

\textit{I should go to the Underground Life and Death Arena starting tomorrow.}

\textit{I need to practice fighting against Transcendent Realm opponents too.}

\textit{So, I'll just rest for today…}

As she lay down again, something suddenly came to mind.

\textit{Ah. I forgot about Female Xiang Ji again.}

As a result of this train of thought, Qing finally confessed to Peng Chaolei about her unintentional impersonation.

"So our Qing'er was the Female Xiang Ji of the Underground Life and Death Arena? I heard that Female Xiang Ji also wielded a dadao?"

"I left it there because it was annoying to carry around. Actually, if I went out with my face covered and carrying a dadao, people would immediately know who I was."

Qing glanced at Peng Chaolei's expression.

Peng Chaolei seemed rather pleased.

"Then, that means our Qing'er already has a Dao Technique she uses? And one that uses a dadao at that?"

"Well, I did learn one along the way. It's called the Blood Shadow Thunder Lightning Dao Technique."

"Oh? From the Royal Demonic Path?"

"Ah! You know about the Blood Shadow Thunder Lightning Dao Technique!"

"Is there a sect that uses dadao in the world that I wouldn't know about?"

To begin with, there weren't many sects that used dadao.

"However, it's curious how you came into contact with the martial arts of those vicious Demonic Cult members."

"I killed a guy who was called a Young Sect Leader and took it from him."

"Excellent!! I happen to have a spare dadao, so why don't we spar? I'll overlook the fact that you impersonated my title. What do you say?"

"Well, I mean, I'd obviously be grateful if you can do that."

After sweating so refreshingly, she felt refreshed and somewhat nostalgic.

Moreover, Peng Chaolei was a good instructor.

The training level of the Blood Shadow Thunder Lightning Dao Technique increased steadily.

And with this, the reason why the sound of clashing steel echoed throughout the Tang Clan compound every day was explained.

"Qing'er, shall we learn about the dao together?"

"I want to learn!"

Clang clang clash.

"Do you know what the largest and most beautiful weapon among all weapons is? It's the dadao."

"The dadao!"

Clang clang again.

"Isn't the name 'dao' cool? It's said to walk the Dao of the Dao\footnote{Another pun. She's saying 'the Way (Dao) of Dao (weapon)}. Among daos, a big dao is called the dadao, so the dadao is truly the big weapon among all weapons."

"Then let's go practice the dao."

Clang clang once more.

"Ah. Is there no one else to share the dao with?"

"I'm right here\~{}"

As the two stuck together and went around like this, there was a woman watching them with tears in her eyes.

"That unworthy thing. This can't go on."

Tang Lan-ah's gaze turned vicious.
