\chapter{Water Knows The Answer (6)}

Tang Lan-ah thought it was an extremely cowardly method.

If one wanted to capture the heart of her sister-in-law, they should boldly flatter her, build friendship through aegyo, and win her over with gifts of rare treasures.

But to resort to something as cowardly as Dao Techniques…

This impacted Tang Lan-ah even greater precisely because she had already witnessed Qing's monstrous strength, swinging people as weapons.

\textit{Hmph. If you have strength, I have poison.}

\textit{Wouldn't it be enough to make Sister lose interest in you immediately?}

It didn't matter whether Tang Lan-ah was plotting such a terrible scheme or not. After all, Qing didn't give a flying fuck. She was just enjoying her training after a long time.

Peng Chaolei was, strictly speaking, an experienced martial artist belonging to the previous generation.

The gap between generations of Rising Stars was ambiguous.

It was originally a phenomenon caused by the hierarchy allocation of prestigious sects.

When Rising Stars settled into positions in their sects, they would pass on the Rising Star positions to the next generation. This happened roughly when their peers did the same, as they also started to have roles in noble clans.

So the oldest current Rising Star was Daoist Changbin (Expert to the female heart, no dating experience, unmarried, 30 years old), and Peng Chaolei, who was about to turn thirty-seven, was one generation senior to the current Rising Stars, having associated with experts of the previous allocation.

With the experience of being one generation senior, along with a higher realm at the Early Stage Transcendent Realm, and superior in pure skill, almost every moment was an extension of a new Dao of the Dao.

Qing's dadao drew a full moon.

Peng Chaolei diagonally met it with an identical-looking dadao, supporting the blade with one hand, causing a hair-raising sound of scraping metal and sparks to fly as the two dadaos rubbed against each other.

The tip of Qing's dadao hit the ground.

Peng Chaolei's dadao instantly changed direction and thrust straight forward, causing Qing to stick close to the ground as if kneeling, letting it pass over her head.

And then… Now!

Qing twisted the handle of the dadao with all her might, attempting a terrifying upward slash with the blade.

However, that attempt was futile as Peng Chaolei's kick to the blade caused the weapon to tilt, twisting Qing's waist.

"An opening!"

Peng Chaolei's fist extended towards Qing's exposed side.

It was a fist imbued with the experience of having broken rocks.

But just before impact, the fist extended its index finger and poked Qing's side.

Qing jumped up with a Kyahehe, an unfinished laugh, and collapsed in giggles.

"This child. It is quite unlike you to be ticklish."

"Kuhup, can't help being ticklish."

"I'm surprised. I didn't see you that way, but you have unexpectedly feminine sides."

"…?"

Qing tilted her head.

Of course, Qing would normally be horrified at being called feminine, but hearing that she wasn't like that made her feel strange.

\textit{Rather than that, isn't my evaluation strangely ungenerous?}

\textit{Why on earth?}

\textit{Does everyone do this once they get a little close?}

\textit{Is there something wrong with my attitude?}

Qing seriously reflected on herself.

The conclusion came quickly.

\textit{I'm always truthful and sincere, though?}

\textit{Maybe this is just how friendship culture is in Zhongyuan.}

\textit{Come to think of it, whether here or there, people usually joke around and laugh together once they get close.}

"That upward slash just now wasn't a good technique. Originally, all weapons have their strengths and weaknesses, and the development of martial arts focuses on utilizing strengths. A dadao should flow from top to bottom, following such a principle, to exert its full power."

"But wouldn't that make it the very definition of an unexpected move…"

"Well, I am not so sure. Since you're also good at wrestling, it might have been better to let go of the dao or throw some dirt. By forcibly turning the blade, your arm was already twisted, so the direction wasn't straight and the power was reduced. Your body opened up with one kick, so you died once. Isn't that right?"

Unlike a certain Mr. Someone from the Nan'gong family, Peng Chaolei didn't pursue only the dadao.

Rather, according to Peng Chaolei, the dadao was a weapon unsuited for the times.

First of all, setting aside the inconvenience of carrying it, being a heavy weapon, it basically had to be handled with both hands, which was disadvantageous compared to other short weapons that could mix Hand Arts or Palm Techniques with the free hand.

Its advantages lay in its long reach and powerful destructive force, but as the level of martial arts rose, these aspects were supplemented through Qi, so the unique advantages of the dadao were gradually dying out.

Yet when asked why she still insisted on the dadao, Peng Chaolei's answer was simple.

‘Because it's the foundation of our family. If it could be easily replaced for convenience, it wouldn't be called a foundation.'

Despite saying this, that Peng guy didn't use a dadao.

"The dao is often said to be Obedient, while the sword is said to Defy Heaven, because the subtleties of these two weapons lie in different places. The dadao moves from top to bottom. It's about flowing like water without hitting the ground and then rising like clouds. It's not all about wielding it with force."

"Oing."

It seemed familiar, and suddenly a Sutra came to mind.

Qing raised her dadao again.

"Let's try again."

"Alright. Come."

Qing flew with the Zero-Gravity Flight of the Yue Maiden Footwork and dropped the dadao forward with a thud.

The dadao, which was falling in a thick stroke, suddenly wavered and collided with Peng Chaolei's, bouncing off at an angle.

At that moment, a sunset-colored Dao Qi suddenly rose up, drawing the shape of falling leaves, and with one clash, there was a loud sound of metal striking four times.

Peng Chaolei leaped back.

"Oooh. What was that? That Dao Technique just now?"

"Uh. It's the Yue Maiden Sword Technique."

It was an application to the dadao of a Sword Style from the latter three Movements that didn't work well with a sword.

"Hmm. The Yue Maiden Sword Technique, is it. It's such an old sword technique. Originally, in those times, swords and daos weren't clearly distinguished, so they were just called 'blades'."

Suddenly, a girl appeared.

Wearing blue clothes dyed with indigo, her hair was disheveled, but she clearly had the lines of a woman.

And so, the girl performed a blade dance, but what she held was not a sword but merely a tree branch.

The girl looked at Qing, smiled gently, and then danced, overlapping with several other images of her as one.

The girl flowed through eight Sword Styles, her dance movements overflowing with joy and excitement, accompanied by clear, ringing laughter.

What the girl held was at once a slender, flexible branch that kept bending and swaying. At other times, a straight, elegant wooden sword. And sometimes, a large trunk of a great tree with many small branches attached.

All could be called tree branches, but their shapes, sizes, and weights varied.

Straight and short ones, curved and long ones, solid ones, elastic and swaying ones. Large ones. Ones with small branches attached. Dried and precarious ones, and ones with just sharp points…

Suddenly, the surroundings turned dark, and the girl became transparent, revealing a figure made of constellations with stars connected to stars.

Dazzlingly bright starlight.

In a place still too far away.

Yet always within reach if one extended their hand.

Suddenly, a semi-transparent rectangular screen appeared before her eyes. Ominous glowing text flickered, and just as Qing was about to reach out and touch it…

Someone poked her side.

Qing turned her head to see the blue-clad girl looking at her and shaking her head.

"Hm?"

"What's wrong?"

"Huh?"

Qing scanned her surroundings.

It's still the Tang Clan's training ground… Then what was that? A hallucination?

Qing looked down at the dadao in her hand.

She examined the dadao closely, swung it around, and tapped various parts of the blade with her finger, listening to the sound.

Qing finally understood the dadao.

Understanding its length, weight, balance, and bias through an unquantified intuition, her heart raced with the desire to draw the countless lines, points, and shapes that could extend from it.

"Let's try again. I saw something."

The ensuing duel was more intense than ever before.

Unlike the previous one-sided instructional sparring, Qing now faced Peng Chaolei with equal skill.

Peng Chaolei summarized Qing's state.

"Congratulations. You've entered the initial stage of Dao Body Unification."

"Dao Body Unification?"

"I don't know why you can't achieve Force Compression despite being on the verge of this Enlightenment. Originally, only after a person knows their body, knows their weapon, and surpasses the realm of handling that weapon as part of their body, can they learn to place the center of their mind in the weapon."

"Ah, I know that! Master said that too. That's Sword Body Unification!"

Qing spoke with a completely clueless expression.

This made Peng Chaolei burst into laughter.

Ximen Surin had already demonstrated Sword Body Unification.

A person holding a sword, yet the person themselves were not visible.

Of course, it didn't mean they were literally invisible.

It was as if her Master was hiding behind that thin sword, or rather, the sword's presence was so strong that one couldn't pay attention to her Master holding it.

It was a strange sight that made one's heart shrink and senses distort just by looking at it.

"I'm not sure, but maybe I'll understand if we keep going?"

"My, my. Look at this child. I didn't see you that way, but you're unexpectedly a born martial artist?"

"What on earth are you even seeing…"

As Peng Chaolei burst into hearty laughter…

"Sister! Ximen Whatever! Oh my, look at that sweat. Aren't you hot?"

With a gentle voice, Tang Lan-ah walked into the training ground.

She was carrying a large tray.

"Training is good, but have something cool to drink. I prepared some snacks."

"Oooh. Something cold. And snacks."

Qing brightened up and plopped down on the ground.

If Ximen Surin had seen this, she would have immediately launched a fierce attack, but the one next to her was Peng Chaolei.

As such, Peng Chaolei also sat down amicably next to her, so there was no one to point out this terrible sight.

"Here, this is for Sister. And this is for Ximen Whatever."

Peng Chaolei placed the portions from the tray in front of them one by one.

Unlike Peng Chaolei's plate, which was clearly neatly arranged, a pile of something roughly stacked was placed in front of Qing.

"Hey, don't discriminate with food."

"Yours has more, you know?"

"I acknowledge this as righteous discrimination."

Qing immediately changed the tune of her words.

After all, decoration wasn't important.

What mattered was taste and quantity.

Qing immediately picked up a large bowl.

The finely crushed ice made a pleasant clinking sound as it shook.

Just as Qing was about to put it to her lips, she lowered the bowl at the sound of gulping.

When looking towards the source of the sound, Qing saw that Tang Lan-ah was staring intently at her.

"What do you want? Are you thirsty?"

"No, no, no, what are you saying? Go on, drink up. It's citron tea with rock honey. It's sweet, sour, cool, and delicious. I didn't add anything else at all."

"Ah. Citron honey tea."

Qing brightened up and downed the citron honey tea.

Having just sweated all over, it felt like her body was absorbing every drop she drank.

"Kyaaah. That's good."

Qing put down the half-finished cold tea and immediately reached for the snacks.

That's when Tang Lan-ah asked with an expectant look.

"How is it?"

"Hm? It's delicious. Cool and refreshing."

"And? Don't you feel anything else?"

Qing tilted her head.

\textit{What's this, is there some secret ingredient?}

Qing put down the snack for a moment and took a big sip of the cold tea, rolling it around with the ice in her mouth.

Sweet, sour, and something… flowery.

"Gulp. I got it. Mint, right? My tongue might not be as accurate as Mister Changzi's, but it's pretty good, you know?"

"Eh?"

"Ah, wait, no. Is it cinnamon? The aftertaste seems a bit spicy too?"

"Eh?"

Tang Lan-ah looked at Qing, seemingly confused.

Then she looked at Peng Chaolei in surprise.

"Ah. Lan-ah, thank you. It tastes good."

Peng Chaolei raised her cup and responded with a smile in her eyes.

Tang Lan-ah grinned.

"Hehe, it's nothing. …Eh?"

Then her expression was full of doubt as she looked back at Qing.

\textit{She looks somewhat stu-, no, like Senior Sister Wannabe.}

\textit{She seemed quite convincing when she was acting as a doctor of traditional medicine. So why is it that she keeps looking like Crutch?}

\textit{Shouldn't her base intelligence itself be in a whole different league?}

"What's with you?"

"Hm? What do you mean?"

"This is strange. Here, let me see that."

Tang Lan-ah snatched Qing's cold tea and gulped it down.

And a moment later.

Suddenly, with a painful groan of Aheuk, she clutched her stomach and started sneezing.

"You, you deceived m-, achoo. Hee, ow, achoo! Ugh. Argh, my stomach, achoo!"

"What the? Are you okay?"

"My stomach hur-, ah, achoo! Achoo! Achoo!"

This time it was three sneezes in a row.

For anyone who had experienced it, they would know that consecutive sneezing was quite painful.

Sure enough, her eyes turned red with tears flowing, and snot dripped from her nose.

Even if she was the Most Beautiful Woman in Sichuan or whatever, there was no avoiding ugliness when she had a contorted expression and tears and snot were flowing.

It was an unavoidable human limitation, after all.

"I, my stomach, ugh, ow, achoo!"

Tang Lan-ah clutched her stomach and got up, leaving somewhere in an awkward, stumbling gait that was urgent yet clumsy.

"Did she eat something wrong?"

Qing muttered as she finished the rest of the cold tea.

\textit{This is really well-made.}

\textit{I should ask for more.}

And so, in the already darkening surroundings, only the sound of sneezing continued, gradually fading into the distance.