\chapter{Water Knows The Answer (1)}

A shadow seeped into the guest room where Ziyou was lying down.

Covered entirely in black clothing, it quietly sat by Ziyou's head, looking down at his sickly face.

Ziyou frowned as he opened his eyes, sensing the presence.

"Old Dog \footnote{犬老/ Quan Lao. Gyeon No (견노) in the original text}, can't you wake me up in a normal way?"

"How could I dare lay hands on Your Highness while you sleep?"

"What if I didn't wake up?"

"Isn't a dog's proper place by its master's bedside?"

Though he referred to himself as a dog, there was no servility in his tone.

After all, Ziyou had been the one to call him Old Dog in the first place.

"Whew. So, how did it go? How did I die?"

"Blood seeped from your entire body, and you breathed your last before anything could be done. Even someone who knows nothing about poison would recognize it as poisoning."

"Tsk. He didn't deserve such a cruel death."

"Wasn't he just a lowlife who crawled around gambling dens? Even if Your Highness allowed it, he enjoyed luxury while pretending to be you. His life was paradise until he died, and even after death, he took Your Highness's place in tragedy. He must have gone to paradise."

"Take good care of his remaining family. I should have something to say in my defense when I meet him in the afterlife."

Ziyou then fell into deep thought.

"I'll have to rely on the Tang Clan for a while."

"Your Highness. Are you saying Your Highness shall stay in this den of shameless parasites who feed on poison?"

"I saw the Tang Clan Lord today. He looked surprised by the sudden intrusion, but not guilty, so the poisoning wasn't the Tang Clan's doing. In that case, is there a safer place in Sichuan?"

"However, they are vile ant-like vermin who dare to nibble away at Your Highness's assets."

"Even poisonous ants seem to have their uses."

Ziyou answered with a faint smile.

That's when it happened.

Old Dog lowered his voice.

"Your Highness, about that young lady. Is she finally going to become the mistress of the royal prefecture? Will this old dog finally be able to serve a mistress in his twilight years? With her beauty that could make birds fall from the sky, if you have a son, he would be the most handsome man in the world, and if a daughter, would she not be the very incarnation of the Most Beautiful Woman Under Heaven?"

Ziyou nodded unconsciously.

\textit{Well, she is beautiful, so if we had children…}

In fact, the children of famous sects or noble clans were all handsome men and beautiful women with an air of nobility from their very appearance.

Since the women of Wulin usually learned at least basic Fairy Arts, this trait had been passed down through generations, raising the overall level of appearance.

Of course, no matter how much attention one paid to appearance, there wasn't anyone who would learn Fairy Arts as crudely and ignorantly as Qing did.

Inner Qi Cultivation Technique were meant to be climbed like stairs in a system, replacing them with higher levels of study.

There were occasional jokes about collecting various types of Fairy Arts to aim for the title of Most Beautiful Woman Under Heaven.

However, if someone actually tried to do so, everyone would try to dissuade them, saying there were easier ways to commit suicide.

"Ah, if this old dog could just see that beautiful child before he dies! I, Old Dog, could fall into a thousand-foot fire pit with a smile."

Old Dog spoke with a voice full of sincere longing.

Ziyou suddenly came to his senses.

He had been worrying about a daughter he didn't even have yet, thinking what if a tyrannical emperor dared to covet her if she was too pretty.

Ziyou waved his hands in surprise.

"No, no. It's not like that. That friend is… She's just a friend. I don't know her character yet."

Ziyou, having grown up in the Imperial Palace, wasn't one to be swayed by beauty.

However, she might be better than the daughters of high officials who were always busy showing proper etiquette and only showed their crown because they bowed so much.

It was only to that extent. Nothing more, nothing less.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was a morning where she was reminded of her Crutch.

In truth, she missed her every morning.

\textit{Having to dress oneself, how could this be?}

\textit{It was so convenient when Senior Sister Wannabe was around…}

Qing, who had woken up late, fumbled to put on her clothes and stepped out of the guest room.

As is usual for guests, Qing had nothing particular to do.

Originally, guests were idle people who stayed and helped only when needed.

If they were there, they were given food, lodging, and even pocket money.

This was why the final goal of all vagabonds was to become a guest at a moderately prestigious government office or noble clan after making a name for themselves.

The vagabonds enjoyed being treated well, and the hosts enjoyed having emergency forces or temporary instructors.

If they stayed for a long time and settled down, they would either become real family or take up a position and become officially affiliated. This was how the culture of guests worked.

Of course, sects or clans that were too powerful and renowned were exceptions.

At that level, they had no need to import outside talent, so they were very selective about accepting guests.

Of course, Qing could be treated as a guest anywhere due to her allocation, but no matter what, she wasn't thick-skinned enough to barge into a completely unfamiliar place and demand food.

That was why Qing had diligently worked as one of the Four Heavenly Kings of the Underground Life and Death Arena.

\textit{Ah. I need to explain about Female Xiang Ji too.}

She had meant to talk about it when the vibes were good yesterday.

But the duck was so delicious that she got completely absorbed and forgot all about Female Xiang Ji and everything else.

\textit{Hmm. The duck was delicious, but…}

\textit{Somehow, I keep thinking about the Ultimate Malatang.}

The Greatest Chef Under Heaven, Bai Changzi, had said this.

Taste is power.

And Qing agreed with him.

Even if his business practices are dogshit, as long as the food is delicious… Is there any more that needs to be said?

If a dish gives more satisfaction than the money spent and the discomfort endured, isn't it unavoidable even if your pride is hurt?

So she thought she should make another reservation today.

In truth, when Qing used to go around with Nan'gong Shencai, the Crown Prince of Anhui Province, they often canceled other people's reservations.

But Qing didn't know the details of those situations.

Moreover, if Tang Lan-ah had brought all her relatives and filled up Azure Dragon, Qing would have just thought it was a company dinner and let it go.

She was only angry because they rented out the whole place for just two people to eat, resulting in her losing her reservation.

As Qing was crossing the Tang Clan compound with Cui Liweng, who had somehow attached himself to her, following behind…

"Ooh, Friend. You're up now? So, where are you going so diligently this early in the morning?"

For reference, the sun was already high in the sky.

"To make a reservation at Azure Dragon. I don't know when I'll come to Sichuan again, so it would be a shame if I couldn't eat there. By the way, who's that person next to you?"

There was an old man standing next to Ziyou.

Ziyou spoke with a somewhat triumphant air.

"Ah. Don't mind him. He's just an old man who takes care of me."\footnote{Chapter 107}

"What? How rude. That's not how you treat an elder. Friend, I didn't think you were like that."

Ziyou looked back and forth between Qing and Cui Liweng in disbelief.

But Cui Liweng had been a Great Demonic Adept before he was an old man from their first meeting.

And even though they had grown fond of each other now, his Evil Karma hadn't gone anywhere.

However, this old gentleman here leaned towards Righteous Karma, even if it was just over ten points, so he was indeed an elder.

"Hello?"

"How can even your heart be as fine as silk? This old servant is called Old Dog, who serves Young Master Ziyou. I am dedicating my life in service to Young Master, who has shown me great kindness."

Even at a quick glance, he was clearly a Master far above her level.

Qing tilted her head.

Normally, Qing was quite confident with handling older people.

But even though it was only their first meeting, he was already looking at her like she was basically his granddaughter.

\textit{What's this? Does this elder have dementia too?}

\textit{Is dementia trending among Zhongyuan Masters?}

\textit{If so, is the future of Zhongyuan really going to be okay?}

"So, where are you going? It's not polite to wander around someone else's house carelessly. Besides, do you know the way out?"

"I guess I just need to go out through the main gate, right?"

"Hmm? Is that so? I suppose you're right."

"I'm going to make another reservation at Azure Dragon. Since I'm in Sichuan, I should eat there at least once. I'm thinking of making a reservation, going to Mount Emei, and then coming back on the scheduled date."

After all, they had to abstain from alcohol for forty-nine days because some Grand Prince or whoever had died anyway.

She was planning to make a reservation well after that, visit the Emei Sect, then have a glass of white liquor accompanied with the Ultimate Malatang before going home.

"Mount Emei, ah. So you have business with the Emei Sect."

Meanwhile, the two old men exchanged glances.

As they were both Masters in the Unrestrained Realm, they immediately recognized each other's realm.

\textit{To use a Master of the Unrestrained Realm as a servant…}

\textit{They must be an incredibly powerful family, so add fifteen points.}

\textit{But subtract fourteen points for being too powerful.}

\textit{It's not good if the in-laws are too successful.}

Cui Liweng ended up giving Ziyou one point.

It was a scoring system as salty as seawater.

Old Dog immediately noticed this.

\textit{Yikes. What a picky old man.}

\textit{Better not offend him unnecessarily.}

The clash between the two Unrestrained Realm Masters ended in Cui Liweng's victory on points.

After all, the one who was at a disadvantage had no choice but to bow in defeat.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Upon stepping out onto the street, to exaggerate a little, it was a sea of tears.

There were even people openly wailing, which Qing found quite strange.

\textit{Is the death of a Grand Prince really that sad of an event?}

Of course, Qing couldn't contain her curiosity.

Ziyou, who heard the question, turned his head away with an embarrassed look for some reason, and Old Dog, who was behind, answered instead.

"Oh my, Miss. Among the people of Sichuan, is there anyone who has not received grace from His Highness?"

Grand Prince Dexian was said to be a person overflowing with virtue, just like his title 'Dexian' suggested.

He didn't collect much in taxes to begin with, and he poured all the taxes he did collect into relief efforts and all sorts of public works. Old Dog went on a passionate rant about how hundreds of lives had been saved because of this and how much the difficult lives of the common people had improved.

"Moreover, he was sensitive to the corruption of officials. After all, didn't he root out all sorts of evil practices that government offices usually engaged in, at least within Sichuan? He was truly a Sage Ruler sent by the heavens."

Thinking about it after hearing those words, Qing realized that the Evil Karma of the officials here did seem to be lower.

"Ah. He was a great person."

"Of course. Not only that, he was full of affection and had great loyalty. If he ever gave his affection to someone, he would cherish them for life and never betray them."

"Ahem, ahem, Old Dog. That's enough."

In any case, Old Dog's words must not have been wrong, as the atmosphere of the city had completely sunk to the lowest lows in just one night.

Everyone looked depressed and made no effort to hide their sadness.

Of course, there was also the reason that showing joy would be treason.

Only outsiders like Qing had puzzled, disgruntled expressions as they wondered whether to go home or not.

However, Qing was undeterred and finally reached Azure Dragon, the Ultimate Cuisine Restaurant where Bai Changzi, the Greatest Chef Under Heaven, lay.

But her efforts to cross Sichuan were in vain, as the door was firmly closed.

"What the… Are they not open…"

"Oh my, Miss, do not be too disappointed. This lowly one will inquire. How dare they, when they should be opening their doors wide and welcoming with bows…"

"It's okay. They must have their reasons. There's no point in causing trouble."

"Ah. Your heart truly is like fine silk. This Old Dog is truly impressed."

At this point, it was confusing whose attendant he was.

Just as Qing was about to turn around with slumped shoulders…

"Oh my! Young Lady! Aren't you the guest who came with that flute, no, I mean, the Speaking Poison Flower yesterday!"

"Oh? Greatest Chef Under Heaven?"

"Ah. I must be right. Since the veil is the same, I could tell."

The one who came running was the Greatest Chef Under Heaven, Bai Changzi.

"What is it? You're not open for business today?"

"Well, I kept checking the ingredients yesterday, and I finally found out the reason. But it's not something that can be resolved, so we closed the restaurant entirely."

"Hm? Was it your restaurant?"

"Not exactly, but if the Greatest Chef Under Heaven says he cannot cook, what can a mere restaurant owner do? Taste is power. If they don't like it, they can cook themselves."

Being the owner of the most prosperous restaurant in Chengdu with the Greatest Chef Under Heaven is a bit too much to be called "mere".

But he was a man whose pride was truly consistent.

"That's all well and good. Anyway, so? You didn't stop me just because you were glad to see me, right?"

"Ah. That. I was wondering if you might have connections with the virtuous experts of the Tang Clan."

"What if I do?"

"It is because if it's the experts of the Tang Clan, I thought they might be able to solve it."

Bai Changzi continued with a serious expression.

"The water, the water has gone bad."

\vfill
\begin{lstlisting}
	The chapter title is a reference to 'The Hidden Messages in Water', a pseudoscience book by Masaru Emoto.
\end{lstlisting}