\chapter{Let's Achieve Slaughter (4)}

It was an expression that Qing really liked.

It was the expression that a bad guy makes when he finally realized that his fate has been sealed.

\textit{Yes, this is slaughter. Yes.}

\textit{It's not a grand act of justice or anything for the good of the world.}

\textit{When you see murderers, cheaters, and other evil people living well, doesn't it make you angry and feel like a thousand demons are rising up inside you?}

\textit{In your mind, you want to kill them a hundred times over, so when you hear that they met a miserable end, don't you feel a smile spread across your face and a sense of relief?}

\textit{But how would you feel if, instead of just hearing the news, you are the one who killed them with your own hands?}

\textit{It's a feeling that's hard to describe, but it's definitely not something you can put into words.}

\textit{This is so good, it's really the best, but I can't explain how…}

\textit{Thank you, Zhongyuan.}

\textit{In a world where private punishment is revered as the spirit of justice, all people praise it and love chivalrous warriors.}

\textit{I'm so happy, no, this is the best.}

Qing said in a strangely excited voice.

"Guys, arms."

At that moment, Peng Daesan and Zhuge Lixian, who had been pressing down Zheng Liuzhang to the ground, simultaneously raised the arms they were holding high.

The shape clearly exceeded the limits of the shoulder joints.

With a crack, the tendons attached to the bones were roughly torn, and the shoulders that had been holding the body let go.

"Ugh! Ugh…"

"Wow, Young Master Zheng! Your shoulders are wider! Your shoulders were so narrow, it was pitiful to look at. So I widened them for you. You will be grateful for the rest of your life."

His dislocated shoulders stuck out, and although his front and back were unbalanced, at least his shoulders were now much wider.

"Kraaah, kill me, kill me! You dogs, I'll kill you all! You bastards!!"

The veins on his forehead bulged, indicating that he was in tremendous pain.

In fact, if you've ever dislocated your shoulder, you know how insanely painful it is.

"You bastards, I'll kill you all, I'll kill you all, Kuaah, do you know who I am, I'll kill you, Huuu…"

Contrary to his previous gentlemanly demeanor, he now cursed incessantly.

However, the curses he uttered were like compliments to Qing.

It's like confessing, 'Teacher, you've really made me feel dirty'.

"Yeah, yeah. Wow, that's so scary. But what can you do? You can't just kill someone with the thought of killing them, right? Wow! That's intense!"

"Kraaah!!"

"What? Are you angry? No, Young Master! This is no time to be angry, but you're cursing like that. I'm hurt."

Qing smiled slyly and stepped back into the office.

"I'm so hurt, Young Master. I have a habit of becoming cruel when I'm hurt. Ah, it hurts. If I pull out that wicked tongue, the wound will heal."

Only then did Zheng Liuzhang's face turns pale.

"Wait, just a moment…"

"But before that, yapp."

Qing suddenly extended her index finger.

The slender finger pierced through the single remaining pupil.

A scream burst out.

She drove her body into her enemy's body (her weapon was also an extension of her body) and feel his condition directly.

The trembling of his muscles, their relaxation and tension, the contraction of his bones, the movement of his tendons, his stiffness, and on the other hand, the convulsions that felt like the violent flapping of a fish caught on a hook…

All these signs of pain were truly like lava burning her spine, and an unbearable tremor spreads through all the muscles of her body.

Of course, Qing don't show it on the outside.

Controlling the body was a basic skill for martial artists, and it's not something to show off to others.

"Kyaaaah!"

However, Zheng Liuzhang couldn't escape where he was pinned down by two martial artists.

He couldn't see anything, and in an instant, he was overcome with fear that he couldn't resist the darkness that had enveloped him, and all he could do was scream at the top of his lungs.

In front of him, Qing spread her arms wide.

Then, she clapped her hands loudly, and with a loud crack!

However, between her hands was the head of the evil man.

For a moment, the only sound Zheng Liuzhang could hear was a loud ringing in his ears.

So, the screams of the wicked, who had created countless sick people with strange diseases and killed their families to make poison, were as rough and mournful as the cries of beasts.

Red blood flowed slowly from both of Zheng Liuzhang's ears, forming a zigzag pattern.

"Ah! Ah! Ugh! Aah!"

Screaming, the wide-open mouth was tightly clamped shut by a strong hand.

Blind and deaf, every sensation was pure terror; reason has long since flown away.

Unable to close his mouth, he chewed on his cheeks, unaware of the pain, and in an instant, his white teeth were stained red with blood.

Qing shoved her fingers into his mouth.

She spread her index and middle fingers, bent them, grabbed the root of the tongue between them, and pulled it hard. 

"Now, this tongue is mine."

Qing threw the tongue she had finally gotten onto the floor of the office.

After all, it's only worth cutting off when it's attached to the enemy's body. Once it's removed, it's just useless trash that can't even be eaten.

"Lan-Ah, give me some hemostatic medicine. It would be a waste if a guy like this died comfortably after bleeding to death."

"Huh? We can use real name?"

"There's no one here listening anymore, right?"

Now, Zheng Liuzhang had lost three of its five senses.

Sight, hearing, and taste.

\textit{Touch, well, I could peel off all his skin… but then he would die quickly, and there is no way to erase his sense of smell.}

\textit{Wait, were there five senses: sight, hearing, taste, smell, and touch? Then what is pain? A sixth sense?}

\textit{No, that can't be. A sixth sense would be a superpower…}

For a moment, the knowledge from her hometown came to Qing's mind, but she knew that no matter how hard she thought about it, she would never find the answer.

Unless she happened to think of it one day while lying down to sleep, there was no way she could confirm it now.

"Ah, that's right. Ugh, how frustrating. Come on, Qing'er. Here."

After carefully sprinkling the powder into his mouth, the trinity of a mute, a blind man, and a deaf man was complete!

To top it off, Crack!

Peng Daesan and Zhuge Lixian twisted the arms they were holding onto by half a turn and let go.

Normally, they would have looked suspicious at Qing's cruel actions and tried to stop her from going too far.

However, they were also very angry.

It was because they've seen the Blood Cult's actions.

They were evil people who spread disease and killed countless people, and then massacred innocent people who tried to save their families with medicine.

Rather, their expressions seemed to show a sense of relief.

近墨者黑. Jin Mo Zhe Hei. Near ink, a person becomes black.\footnote{Chinese idiom, first attested in Taizi Shaofu Jian.}

This was why adults always tell us to choose our friends carefully.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When the Blood Cult warriors rushed to the scene, they found the entrance to the mine spewing black smoke.

They had rushed out to prevent the fire from spreading to the mine, but what if the mine itself was on fire?

For the moment, they could only stare blankly.

They were confused, and seeing the mine in flames, they had no idea what to do.

"Captain, the mine…!"

The man called Captain quickly regained his senses.

"You bastards! Instead of protecting the mine, you let it catch fire! Poison Demon ordered me to take special care of this place! We must block the entrance immediately! You, take these three and fill these sandbags. You, pick up rocks. Hurry!"

If a fire broke out in a coal mine, there was only one way to extinguish it.

By piling stones and dirt at the entrance to block it tightly, the people of Zhongyuan at that time knew that even if they didn't know the exact principle, the fire would be extinguished if the air couldn't get through.

However, if Qing saw this, she would laugh and say, 'I knew it. Are you worried about this fire?'.

The miners who have settled at the mouth of the mine were not concerned about the safety of their fellow countrymen, but rather about the special orders of Poison Demon, which was probably the Corpse Poison factory.

Even then, they seem more concerned about the puinishment from Poison Demon than the poison factory.

The soldiers immediately brought shovels and burlap sacks and began working busily.

Martial arts training was advantageous for manual labor, as it gave one strength to dig, flexibility, and large movements, and allowed one to hold one's breath and maintain one's breathing even when approaching the entrance of a mine filled with acrid smoke.

They were the best workers, the finest talent that would make the supply officers' eyes in Qing's homeland light up.

Thus, obstacles began to pile up at the entrance of the mine.

The warriors who arrived later joined in and sped up the work.

Meanwhile, inside the mine, in a shallow area.

A suspicious bag was lying on the ground, and a thin rope was sticking out of it, leading deep inside.

And if one were to follow that rope?

Beneath the acrid smoke, a small flame could be seen slowly burning along the long rope, making its way toward the outside.

The flame continued to burn slowly, eventually consuming the rope and disappearing into the bag.

At that moment, with a loud bang, the gunpowder explodes, and a considerable amount of fire rises.

Then, smoke billowed up from the bag and disappeared into the black smoke of the mine.

The Blood Cult warrior who was stacking sandbags coughed violently.

"Ugh, cough! What's so spicy…?"

"Sung Chang-eura, don't inhale the smoke."

"Cough! Cough! Guh! Ugh, ugh, ugh."

However, unable to do anything about the smoke they had already inhaled, the Blood Cult warriors staggered and eventually collapsed, coughing incessantly.

Another Blood Cult warrior clicked his tongue, grabbed his comrade under the armpits, and dragged him out of the smoke.

"What's going on there?"

"I think he inhaled too much smoke."

"Tsk. We need all hands on deck. Give him some water and lay him down somewhere far away. A martial artist can't even control his breathing?"

The captain clicked his tongue in disapproval, but then he saw the blood and froze.

"What's wrong with him?"

"What? Oh no!"

The Blood Cult warrior looked down at his fallen comrade and saw the foam boiling at the corners of his mouth. He was shocked and stepped back.

At that moment, the warriors blocking the mine entrance began to stagger and fall one by one.

"Damn it, what are you all doing? Save the kids first!"

The captain rushed in and grabbed the warriors by their arms, dragging them away.

However, they were all foaming at the mouth, their eyes rolled back, and the whites of their eyes were showing.

The captain's face turned pale.

\textit{These are typical symptoms of poisoning. Could there be a fire in the poison factory? If it was smoke mixed with poison…}

"Poison gas! Poison gas! Everyone back away! Cover your mouths and noses!"

The captain made the best decision he could.

If poison gas was already escaping from the poison factory, then their mission was already a failure.

Rather than increasing the number of unnecessary casualties, it would be better to let the mine collapse naturally.

The wrath of Poison Demon was frightening, but since the fire started in the poison factory underground, it was highly likely that it was the mistake of the poison maker who was manufacturing the poison.

Of course, the Blood Cultists were still alive and kicking in the poison factory, and it was just a matter of setting up the poison that Tang Lan-Ah had with her.

In case the fire was extinguished sooner than expected, they mixed poison into the smoke to delay the extinguishing process.

The slow-burning poison was not very toxic to begin with, and in fact, it was a poison that could be cured by getting some fresh air and resting for a while.

However, from the perspective of the Blood Cult warriors, who did not know this, it was an unavoidable decision.

Thus, as thick black smoke billowed from the mine, the sound of thunderous footsteps echoed throughout the mine.

Finally, there was a loud rumbling sound!

It was a dull sound that was heard more by the soles of the feet than by the ears.

The inside of the tunnel had collapsed.

It was the moment when thousands of pounds of soil mixed with coal and boulders fell onto the iron plates covering the vertical passageway leading to the Corpse Poison manufacturing facility.