\chapter{Let's Achieve Slaughter (5)}

Among the scum of the Blood Cult, the strongest among them cried out with all his body.

With a solemn expression, his mouth tightly shut, he lay down and wriggled, crawling forward on his stomach with his stomach exposed.

This was a method of swimming with the left and right shoulders, so Zheng Liuzhang with broken shoulders must be in tremendous pain with every wriggle.

Even so, he gritted his teeth and somehow make his way through the quiet world of darkness that cannot be seen or heard.

Even in this state, his desire to live and their determination to survive could be seen as a scene worthy of applause, a celebration of humanity.

However, this would only be true if the perpetrator was not an evil person who deliberately spread the plague and slaughtered nearly a thousand innocent people.

In any case, wasn't his will to survive, to secretly escape from this place, truly remarkable?

Of course, he couldn't overcome his lack of sight and hearing, so he was crawling toward the dead-end wall of the office, which was very amusing to watch.

\textit{Hmm, gouging out the eyes and piercing the ears was more miserable than I thought. Ha, this is exactly what it means to value human life and not kill indiscriminately. Should we actively adopt this practice in the future?}

Unaware that Qing was glancing at him and smiling, Zheng Liuzhang desperately moved forward.

The pain in his shoulders was indescribably terrible, and his gums ached from clenching his teeth, but he had to survive.

It was then.

Thud.

Something sharp stabbed his nose.

"Huaahhhhhhhhhhhhhhhhhhhhhhhhhhhhhh"

A scream of pure terror erupted.

He couldn't see or hear anything, and in the silent darkness, something was tapping his nose, and the feeling was so terrifying that he was overwhelmed by a panic attack caused by the unknown.

\textit{What tapped me? Did someone catch me? Was I stabbed? It feels like it's burning, or maybe it's poison? It feels strange, but I don't want to die like this…}

In front of Zheng Liuzhang who was trembling with fear, a small child was holding a tree branch and giggling.

The shadows under the child's eyes, which were unusually tired for her age, made her look cute.

It was Ciyu.

"Hehe."

Ciyu reached out her hand, but—

"No, you can't. That's dirty."

"Ung…"

"Don't touch it with your hands. Blood Cult is dirty, you know?"

"Yes. Hehe…"

Ciyu poked Zheng Liuzhang here and there with a long tree branch.

Each time, Zheng Liuzhang jumped up in fright.

Ciyu giggled, and her eyes, which had always been dull, sparkled for once, revealing her childlike innocence.

Qing saw this and secretly sighed.

She wondered if it was right to let her daughter eyes sparkle at a time like this.

But Ciyu had every right to do so.

She had the right to take revenge on the Blood Cult.

Jian Buxi stood close to her niece, smiling happily and asking, "Is it fun, niece? Do you want to try here too?"

She showed her affection for her niece by pointing here and there on Zheng Liuzhang's body.

"Hmm. Lan-Ah. Is there a prescription in the secret documents?"

"Yes. Jeongyak, Pasinchu, and Donghacho are effective? Or maybe Gadamyeop? But it's rarely used for medicinal purposes. There are others too."

"If the current pandemic is not a plague but a symptom of poisoning, it could be that the Blood Cult spread it, so they may have used poison. In that case, it would be difficult to treat with normal medicine."

"I see."

"Hmm, then we'll have to return to Langzhong Daren and get a new prescription made. It seems impossible to get medicine from the Blood Cult."

With that, Qing rubbed her chin.

"We should inform the Diancang Sect of the current situation, right? The Blood Cult may have infiltrated other places besides Five Poisons Sect."

"You're right, Sister. Given the circumstances, shouldn't we consider the rumor of the Bai Plague to be a plot to sow discord between the Bai and other ethnic groups? And those spreading these rumors are either members of the Blood Cult or connected to them, so we may be able to track down a large group of Blood Cult members."

"In that case, either way, the situation is urgent, so we should split up and head to Diancang Sect and Kunming. Zhuge need to explain the situation to Diancang Sect, and um, I think Ciyu should stay in Diancang too. Can you take her and Yi-mei there?"

"Sure."

"Lan-Ah should go to Kunming to help Langzhong Daren. We don't know what the Blood Cult will do, so San and Iri should go with you."

At that, everyone's eyes turned to Qing.

Qing burst into a clear laugh.

They were asking her where she was going.

\textit{What are you, ducklings following their mother?}

\textit{Oh, you guys still aren't close enough?}

\textit{Do you feel like you're friends with my friends when I'm not around?}

\textit{Actually, I like it.}

\textit{It makes me feel a little more at ease.}

\textit{I think I can tell you this much.}

"Guys, actually, I have something to tell you."

Qing moved her lips. Again and again.

\textit{Hmm, now that I'm about to tell them, is it okay? That I'm different from them, that it's just the way people are, that's why.}

Qing hesitated.

Seeing Qing unable to open her mouth, the expressions of the others also became serious.

That was understandable, as Qing was always the type to speak her mind without knowing how to hold back.

But now, Qing was hesitating.

What difficult topic could it be that she wanted to say?

"Actually…"

Qing opened her mouth again.

At that moment,

Her hands, which were unusually cold and sensitive to the warmth of others, were touched by warm skin.

Qing turned her head in surprise, and what a rare sight it was.

Xue Iri was looking at her with a rare, elegant smile.

Then, Tang Lan-Ah quickly put her arm around Qing and leaned against her.

"No, that's just her being a fox again. Ha. Qing'er, I'm not even curious in the first place. I don't care about anything."

Peng Daesan also avoided her gaze and muttered, "She wasn't normal from the beginning."

Zhuge Lixian too-

"Sister, why are you being so cold to us now? Even if you have mastered an evil Demonic Art, or even if you have mastered all of the Ten Great Demonic Arts, you are still the leader of our Half-Sword Double-Saber Association."

Qing's heart skipped a beat.

\textit{What? What does that mean? Does he already know?}

Zhuge Lixian was just assuming the worst and saying something meaningless, but in Qing's homeland, they said that thieves always trip over their own feet.

\textit{Still, maybe it was just a worry for nothing.}

Qing revealed the secret she has been harboring for a long time.

"I actually have immunity to all poisons."

"…?" "…?" "…?" "…?"

Everyone was confused by this unexpected revelation.

"What?"

"Myriad Poisons Immunity. All poisons in the world are ineffective against me. San, you don't know Myriad Poison Immunity? You don't know much, do you?"

"No, that's not it. Ha."

Peng Daesan let out a deep sigh.

He sounds like he was worried for nothing and suffered a loss.

"So, you're saying that you've achieved Myriad Poisons Immunity?"

"It's not like I achieved it, it's just the way I've been since I was born. It's just my constitution."

"Oh, um. That's an incredible constitution."

Zhuge Lixian nodded with a sour expression.

"What the heck? You guys, if that's what Qing'er think, then so be it. I believe you, Qing'er. Our Qing'er has immunity to all poisons? Wow, that's amazing."

\textit{Hmm. At least there's one person pretending to believe me.}

Qing turned her head away.

Nod.

Xue Iri remained expressionless and stern, simply nodding her head once.

\textit{No, I tried so hard to say something.}

\textit{What kind of response is this?}

"Hey, I'm telling the truth."

"Hmm."

"Lan-Ah, you have poison, right? Give me the strongest one, or better yet, give me all of them. I'll swallow them all so you'll believe me."

"No. I believe Qing'er. Okay?"

"Aishhh."

Qing scratched the back of her head.

But that didn't last long.

"Anyway, I think I'll keep an eye on the Five Poisons Sect. I'm immune to all poisons, so the Five Poisons Sect is no threat to me. I fought against some of those guys in Sichuan, and they weren't particularly threatening. So, you guys go to Diancang Sect and Kunming, and I'll take a look around the Five Poisons Sect while you're gone…"

Everyone looked at Qing with a 'That makes sense' expression.

"You're going alone again?"

It was Peng Daesan's low-frequency voice, which Qing hadn't heard in a long time.

Seeing that he hadn't use the ultra deep frequency, Qing realized that he wasn't angry yet.

"No, it's not that I'm willing to take the risk alone this time, it's just that there's no risk in the first place. You all know that if you have immunity to poison, you don't have to worry about the poisoners, right? Once the poisoner ran out of poisons, all that's left was beating up the poisoner."

"Sister. I told you before…"

"Damn it. You guys don't believe me when I say I have immunity to poison, do you?"

That was only natural.

Myriad Poisons Immunity was not a real thing.

In fact, the people of Zhongyuan were braggarts who made up things that no one had ever achieved.

What about the ridiculous claim that they could kill anyone with their mind if they wanted to?

Even if you reach the ultimate level of poison, called 'poison human', where deadly poison flows through your veins, it doesn't mean that all poisons in the world were ineffective.

It just means that most poisons were ineffective, but even miscellaneous poisons that were incompatible with each other can disrupt the body's balance of toxins and cause self-destruction.

You might say that the weakness of someone who has reached the pinnacle of poison arts was too weak, but how terrifying was a human being who was so poisonous that even a splash of blood in a fight can cause poisoning?

Of course, a master of Hyung-kyung can suppress the poison with their Inner Qi and expel it over time, even if they were poisoned by a well-known poison.

Therefore, when one reaches the level of natural mastery that transcends the realm of the mortal world, poison would not affect them at all.

This realm, which was created through the collective efforts of many, was called 'Myriad Poison Immunity', a body that was immune to poison.

For this reason, it was only natural that the group did not believe Qing.

Even if there were countless people and countless body constitutions in Zhongyuan, where could one find a person who was immune to all poisons?

No matter how many people there were in Zhongyuan and how many different constitutions there are, where on earth was there a person who was immune to all poisons?

"Lan-Ah, take out the poisons."

"Eh, Qing'er is a Harmony Realm Master, so even if she was poisoned, she can hold it in, right…?"

"Since you're a member of the Tang Sect, you must have some really strong poisons, right? Like the Seven-Step Soul Severing Sand? They say you'll die before you can even take seven steps, right?"

"Eh, Qing'er. I'm fine. I believe you, so why bother? It'll be fine, right? Wow. Myriad Poisons Immunity. That's amazing."

"No, it doesn't sounds like you believed me…"

Then, suddenly.

Xue Iri, who was holding Qing's sleeve, shook her head left and right.

The veins on Qing's forehead bulged.

\textit{No, they don't believe me at all.}

"No, honestly, it's not like before where it was my own affairs and you guys didn't have to worry about it. I'm not putting myself in danger or anything."

However, the others were still unsure.

Qing pounded her chest, no, she pounded it hard.

"Look, I'm not telling you to stay somewhere safe. Zhuge, you explain the situation to Diancang, and Lan-Ah, help Lanzhong Daren. San and Iri, protect Lan-Ah and Elder, just in case the Blood Cult try something. I'm leaving it to you, am I not?"

Qing felt wronged.

She trusted them and left them in charge, but now they were treating her like this.

She hid her Myriad Poison Immunity because she was afraid of being treated strangely, but now they didn't even seem to believe her.

\textit{You, me, us, was that right? Isn't this nonsense?}

"Lan-Ah, you have that poison that makes eyes and nose waters, right? Give it to me. I'll eat it, and then you can take turns taking my pulse to see if I use my Inner Qi or not."

Her companions looked at each other as if they were conspiring against her.

'If Young Lady Ximen said so, it doesn't sounds like a lie, right?'

'Regardless of whether it made sense or not, Sister's abilities are beyond comprehension in the first place.'

'Huh? I feel like I'm about to remember something.'

'Well, she was saying she wouldn't leave us behind. Hmm.'

And then they seemed to come to an agreement.

"All right. Come to think of it, you haven't lied to me in a while."

"As expected of you, Sister. You're amazing. Myriad Poisons Immunity? You are truly a blessing to the Orthodox Wulin."

"Ah! That's right. That time too."

Tang Lan-Ah slapped her palm with her fist.

A scene from the past suddenly came to her mind.

\textit{When Qing first entered the Tang Gate, we were the best of friends with no secrets between us, and we used to play very minor pranks on each other to relieve our stress.}

\textit{At that time, Qing playfully turned the tables on me, and I ended up getting hit.}

If Qing heard this, she might say that it was a bit distorted, but people's memories were subjective in the first place.

"Now, you understand, right? Yi-mei, take good care of Ciyu. Ciyu, listen to your aunt."

"Yes." "Yes."

Anyway, that's how it is.

The Half-Sword Double-Saber Association, each headed toward their respective positions.