\chapter{Let's Achieve Slaughter (1)}

Sometimes, there were mornings like this.

You wake up naturally, open your eyes, and find that it was an exceptionally refreshing morning.

The sleepiness disappears naturally, your body was full of energy, and you get out of bed with a clear mind, not regretting the time you spent sleeping. It was the start of a pleasant day.

Today, that was Zheng Liuzhang's morning.

In fact, such a refreshing atmosphere was not a once-in-a-lifetime stroke of luck.

It was simply the vitality provided by the anticipation of a new day and the desire to welcome today as soon as possible.

This was also why people in Qingju, the hometown of the Qing family, don't want to get up in the morning.

That's why the morning at Zheng Mansion was so refreshing.

\textit{First of all, there is no particular work to do at Zheng Mansion, so I just show up as the head of Zheng Family, and the grand plan of Our Cult is sailing smoothly like a ship with a favorable wind.}

\textit{And above all, didn't the Demon King send word that he was ready to welcome that insolent woman?}

\textit{In particular, the merciful Poison Demon said that even if she iss covered in poison, he will bring her to me if I wish.}

\textit{A captain never forgets a grudge, and every moment was thrilling as I think about how to punish that woman.}

\textit{Yes, what will I do when she was brought to me?}

\textit{To break her arrogant pride and make her beg for mercy, I will raise her in a pigsty filled with animal excrement, torture her, and then, in the end, make her kill her own friend, cleanly cut off the flesh, and eat it, promising to spare her life.}

\textit{And then I'll cut off her flesh and slowly enjoy the look of despair and self-blame on her face…}

Just as Zheng Liuzhang was grinning and refining his torture plan,

"Young Master, there's trouble!"

Bang! The door was opened so violently that it flew off its hinges and began to fall.

When Zheng Liuzhang frowned and was about to speak, the servant who appeared through the broken door said,

"Right now, the sky was black with smoke. There seems to be a big fire!"

"Fire!? What do you mean, fire? A forest fire? Where? Where? It can't be Mount Laoyin, can it?"

Mount Laoyin was located east of Zheng Mansion, behind the city, and was also home to a coal mine.

"It looks like it's Mount Laoyin…"

"A fire out of nowhere! No, I have to see it with my own eyes."

Zheng Liuzhang rushed outside.

Even without looking up, half of the sky was already covered in black smoke.

From the eastern sky, a black column with a acrid texture rose toward the sky, billowing from its rough surface.

Zheng Liuzhang was stunned by the majestic scene.

But that moment was short-lived. He shouted, "Mine! What about the mine!?"

"W-We don't know. The smoke is too thick, so we can't see the flames yet."

"What the hell!? Are you going to just stand there and watch until the mountain burns to the ground!? Mobilize all available personnel! Block the entrance and destroy all the lodgings to prevent the fire from spreading to the mine!"

"Yes, sir!"

The subordinate hurriedly ran away.

Zheng Liuzhang chewed his lips anxiously.

\textit{Of all times…!}

\textit{The first harvest of Corpse Poison had not even begun yet.}

\textit{If the fire spread to the mine shaft, it would collapse in no time, and all the Corpse Poison that had been carefully cultivated would be buried.}

\textit{With the grand plan of the sect just around the corner, of all times!}

Zheng Liuzhang never thought that a fire would broken out in the mine.

Not only him, but no one at the Zheng Mansion thought there was any possibility of a fire in the mine.

After developing the coal mine as to supplement the funds of the Blood Cult, they discovered a natural cave that was perfect for making Corpse Poison, and since then, they had stopped mining coal altogether.

It was Poison Demon's order, out of concern that a fire might break out in the mine.

There was no way a fire could break out in a mine where no one went, so it must be a forest fire.

Soon, bells rang and whistles sounded here and there.

The Blood Cult's reserve warriors rush past Zheng Liuzhang, and soon, silence envelops the deserted estate.

Zheng Liuzhang, left alone in the middle of the estate, was anxiously biting its nails.

A woman with a gentle and kind voice called out to Zheng Liuzhang.

"Young Master, I'll tell the kitchen to clear away your breakfast."

"What? What are you talking about? What nonsense are you talking about?"

"You've been biting your nails, so you must be full already. Here, I've brought you something to drink."

The woman, with her hair neatly combed, offered him a cup with a friendly smile.

"What is this? I don't need it! Who asked you for water?"

"Aren't you thirsty? Your fingernails are black from biting them. Even so, I thought you might be thirsty because you ate something salty."

Contrary to her gentle and kind demeanor, every word she said cut deep.

Perhaps because of that, Zheng Liuzhang's gaze was filled with nothing but contempt.

"Oh, my arm is going to fall off. Aren't you going to drink it?"

"I'm not busy, so just get out of my sight."

"Oh, I see. Congratulations."

"What? In this situation, congratulations?

"What? Of course I should congratulate you. Today is the day our Young Master achieved the legendary state of Myriad Poison Immunity."

"What nonsense are you talking about?"

"That's strange. There is a forest fire, isn't there?"

"What's wrong with the forest fire?"

"There's a forest fire, and the mine is in danger, but you didn't order me to report to Poison Demon."

There's a forest fire, and the poison manufacturing facility was in danger.

Of course, he had to report it to Poison Demon.

But since he was not going to report it, he was not afraid of Poison Demon anymore.

To not be afraid of Poison Demon, one must achieve Myriad Poison Immunity.

"Of course, Poison Demon's poison is scary, but it may not be necessary to achieve Myriad Poison Immunity. Still, you need to at least achieve Thousand Poison Immunity to be able to fight him, right? Hmm, but it is Poison Demon's poison, so Thousand Poison Immunity may not be enough. Then you would need to achieve Five Thousand Poison Immunity, right?"

Zheng Liuzhang flinched.

"Ahem, I just wanted to report after getting a clear picture of the situation."

Zheng Liuzhang replied, then, as if his throat was parched, he grabbed the woman's bowl and gulped down its contents.

Then, puff! He immediately vomited violently.

"Cough, cough, ugh, ugh. Ugh, you, you, what did you feed me, ugh."

"You always have a bad smell coming from your mouth, so I just mixed in a little vinegar."

"Cough, cough, cough! It's not just a little, ugh."

"Oh dear, shall I pat your back?"

"No, go away! Get out of here! Get out!"

Zheng Liuzhang waved his arms and yelled.

The woman smiled even more kindly.

"But you look very weak. There are only a few people left at the estate. What will you do without me? You are only being treated well because you are the son of the Captain of the Royal Guard, but you were a weakling who thinks he was smart."

"Get out!"

The woman smiled brightly.

Then she bowed deeply.

"I will obey your orders. Then, you must behave yourself. Otherwise, you will die."

"I will take care of it myself, so get lost, you monster. And I have already prepared fire tools in case of an emergency at the mine, so even if the fire spreads—"

"Oh. I wasn't talking about the mine, was I?"

"What?"

"Well then, I will grant your wish. I must be going now."

"Wait!"

Zheng Liuzhang tried to stop her, but he clamped his mouth shut.

The woman had already disappeared.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The door of Zheng Mansion opened, and a group of people rushed out, each carrying various tools.

They were in such a hurry that they didn't even form a line, and the gap between the front, middle, and rear of the group was widening.

Judging from their clumsy movement arts, the ones at the front must be second-rate fighters. If the leaders were like this, what must the rest be like?

In the bushes at the foot of the mountain, Qing carefully observed them with narrowed eyes.

\textit{Hmm, that station, or was it a bus stop?}

\textit{In any case, that's what the name sounded like, but I don't see that guy.}

\textit{But if their power is that weak, we should had just attack them head-on.}

\textit{However, you can never be too careful, right?}

\textit{Of course, that doesn't apply to me, as I'm unlikely to be threatened, but it does apply to the other members of the Half-Sword Double-Saber Association.}

\textit{So, let's raid an empty house.}

\textit{We waited so hard until morning, but what do we find? The power is even weaker than I imagined.}

A moment later.

The door of Zheng Mansion closed.

Qing finally get up from the bushes.

"Let's go."

The expressions of the group heading toward Zheng's Mansion were grim.

The main gate of Zheng Mansion, which hadn't even been reinforced, showed no signs of anyone having been there.

Qing stood in front of it and banged on the tightly closed door, shouting.

"Come out! Can't you come out?"

With each blow, the door bent inward as if it were about to break.

Even so, the door did not fall off, thanks to the new hinges installed by Ximen Qing, the civil engineer.

\textit{What? He installed new hinges? How dare he, a member of the Blood Cult?}

Bang, bang, bang, bang!!!

It was almost like the sounds of a riot.

How long did Qing banged on the gate of the empty Zheng Mansion?

A voice came from behind the door.

"Sir, we were not receiving guests at Zheng Mansion right now…"

Suddenly, Qing's eyes flashed.

With her shoulder blades almost touching her back, she spread her arms wide, leaned back as far as she could, and spread her palms.

Finally, Qing took a big step forward and stretched out her arms.

Bang! The gate shattered with a loud noise.

Large and small fragments flew like buckshot.

The Blood Cult member behind the door was thrown away with his waist bent, and the fragments cut through his clothes and skin, embedding themselves in his torso.

As the Blood Cult member rolled on the floor, covered in blood in an instant, Qing strode across the room.

"Who… who is it?"

Deeng! Before the person she encountered could finish his sentence, a magnificent bell rang out, and the old Blood Cult member collapsed and trembled.

It was because the formidable power of Tathagata' Divine Palm had crushed his chest.

The shine in Qing's eyes faded a little more and sank into a deep abyss.

The Blood Cult members in the mine came to her mind.

\textit{They weren't innocent, but they were pitiful lives that could be sympathized with.}

\textit{The commoners who were born in the village of the Blood Cult, who were too scared to even cry or resist, were just born there.}

\textit{Why, why wasn't I happy?}

If they had cursed her with all their might and rushed at her with hidden daggers, Qing could have laughed at them and cut them down with pleasure.

\textit{Is that why? Is it because I had cut down such powerless opponents who couldn't even dare to resist?}

\textit{Because they had never even held a weapon, let alone practiced martial arts?}

\textit{No, that can't be it.}

\textit{I have slain countless unskilled men, and reducing my opponents to a helpless state where they could not fight back was the ultimate slaughter.}

\textit{Or is it because they were people who didn't need to be killed?}

\textit{No, they had to die.}

\textit{If we let them live, they would report us to the Blood Cult and have them come after us, and even if they didn't, they would end up working hard for the Blood Cult again, brainwashed by hatred.}

\textit{Then why do I feel so uncomfortable?}

\textit{Because I killed women? No, that's not it.}

\textit{There is no gender distinction in the face of evil. Who else practices gender equality as much as I do?}

\textit{Killing the young? That's not it either.}

\textit{Those with no future will continue to harm the world for the rest of their lives, so they were worse than old evildoers.}

\textit{Yes, they are people who had to be killed.}

\textit{Even so, dealing with the Blood Cult members in the mine was just unpleasant, and even though I cut their throats without pain, I felt bad the whole time.}

\textit{It wasn't slaughter, it was disposal, mechanical work, something like that.}

\textit{But after pushing the severed heads into the hole and disposing of them, the mournful cries coming from below were truly sweet.}

\textit{When we set fire to the mine and left, the screams of the dictator we left behind, the curses of the woman whose limbs had been mutilated and left to burn alive, were music to my ears.}

\textit{But why?}

\textit{Killing the servants of the Blood Cult wasn't fun at all.}

\textit{It is the same now.}

\textit{All the strong men had already been taken away.}

\textit{Killing the Blood Cult members I encountered, the old men and women who were not called to duty, is not enjoyable at all. In fact, it is unpleasant.}

\textit{The more I do so, the more my unresolved anger and burning rage stuck to me, burning my insides.}

\begin{lstlisting}
	The chapter's title is another reference of 1947's South Korean song, '우리의 소원' (Our Wish)
	
	This is the song first verse:
	Our wish is unity
	Even in dreams, wishes are unified
	Unity with all this sincerity
	Let's achieve unity
\end{lstlisting}