\chapter{Let's Achieve Slaughter (2)}

Qing passed through the round passageway on the wall of the Zheng Mansion.

Then, her eyes met those of Zheng Liuzhang.

It was because the dull sound of a temple bell was getting closer and closer.

If you have ears, you would naturally want to go outside to see what was going on.

However, if Zheng Luzhang had known about the miraculous power of Tathagata's Divine Palm, he might have noticed the danger approaching him.

Their eyes met, and seeing the look on his face, as if to say, 'Why are you coming out there?', he must not have known.

This was precisely why one must know—knowledge was power, and the countless admonitions of the sages that one must learn to survive existed for this very reason.

"You, how did you, you didn't go to Five Poison Sec—"

"This house is terrible at welcoming guests! Whether you're happy to see them or not, when guests come, you should first ask a servant to show them to the guest room and serve them tea and refreshments, right? Isn't that right, Young Master Zheng? Don't you know even such basic manners?"

Surprisingly, Qing's words were correct.

When receiving guests, one should not discriminate, and even if the guest was someone you dislike, you should first treat them as a guest and deal with any issues later.

And such righteous words were the most annoying thing to hear.

How could someone who was clearly an unwelcome guest complain about the hospitality?

Zheng liuzhang's forehead veins bulged.

Then Qing pretended to be cheerful.

"What's all the commotion? There's been black smoke rising since morning. It looks like a fire, but the gatekeeper isn't even guarding the gate. Could it be? There's a coal mine over there, right?"

"It's probably just a forest fire. The coal mine was thoroughly prepared in advance. There are workers there, and all the laborers from the estate are mobilized, so things are a bit chaotic. Please understand."

"Ah, so that's why the reception was such a mess. Well, I'm a generous person, so I'll understand. Be grateful."

"No, what the—"

"Ah, I stayed up all night and didn't eat breakfast, so I'm starving. Bring me a hearty breakfast."

"No."

"Everyone worked hard all night. You must be tired from moving and running around. No one showed us to our rooms, so let's just go in and rest. Ah, that place looks perfect."

"No. Hey, what are you doing? No, even if you say so, no."

Zheng Liuzhang was dumbfounded and left speechless.

Regardless, Qing walked briskly into the master room.

Then, she sat down on the seat of honor and put her feet up on the desk.

This wasn't the first time Qing had behaved like this.

Moreover, her companions understood that there was a good reason for Qing's behavior.

So they followed Qing inside and found places to sit.

Tang Lan-Ah picked up a chair and placed it next to Qing.

Then, she sat down, leaned against Qing, and naturally wrapped her arms around her.

Xue Iri naturally approached Qing and squeezed in next to her.

The chairs placed at the head of the table in Zhongyuan were usually just wide enough for one woman to sit comfortably.

Therefore, they were usually occupied by concubines, young children, or grandchildren.

"Hey! What are you doing? Why are you squeezing in there when there are so many seats available? You're really a funny girl."

"Sit down. There's no seat. Yes."

It was Xue Iri as usual.

What were you doing? Sit down.

Why were you squeezing in there? There's no seat.

You're a funny bitch, aren't you? Yes, I'm funny.

"Why isn't there any space? Are you blind? That's not a chair, it's a decoration."

"Yes. Yes. Yes."

Why isn't there any space? There isn't any.

Are you blind? Yes. What are you going to do about it?

Is that chair a decoration? Yes. It's a decoration.

Tang Lan-Ah's forehead veins bulged.

She was now accustomed to Xue Iri's way of speaking, but it was becoming increasingly effective at getting under people's skin.

Using honorifics when arguing was also part of that.

Tang Lan-Ah stood up abruptly and grabbed Xue Iri's arm.

"Hey, aren't you coming? Why are you so heavy… Hey…!"

Unlike Tang Lan-Ah, who was pulling with all her weight, Xue Iri was quite calm.

Then, she said something with triumphant tone.

"This body, master."

"Aaahhh! I really hate you!"

"Me too."

Tang Lan-Ah trembled, but soon, with the unique baggy sleeves that were the symbol of the Tang family and the pockets of Wuhan, she displayed her exquisite handiwork, spreading out her Golden Hand technique.

'Ohhh.'

Qing murmured in admiration.

Lan-Ah was the worst of the worst when it comes to martial arts, but her handiwork was quite useful.

Of course, in front of Qing, who had mastered Divine Thief's divine skill, pickpocketing techniques, and the divine beast technique, it was a rather clumsy trick.

"Oh, come on. That's no good. Don't you know the three things you should never use between friends? Knives, poison, and collaterals. Underline the last one. I told you many times."

"But, that's…"

"Put it back."

"Why, why only me? See, she stick out her tongue again? How could you do this to me? I was your friend first. This isn't right. How could you do this?"

A wet, whiny voice burst out of Tang Lan-Ah's mouth.

Qing sighed deeply.

"You're not a child. Come here."

When Qing opened her arms, Tang Lan-Ah, as if nothing had happened, threw herself into them with a bright smile.

The expression on Zheng Liuzhang's face as he watched them was one of utter bewilderment, his mouth wide open.

There was no such thing as this kind of behavior.

A guest barged into the Master's office without permission, took the seat of honor, put her feet up on the desk, and held women on both sides.

Of course, it was not unusual for women to hug and embrace each other when they were together.

Zheng Liuzhang's mouth opened and closed.

The others pretended not to notice Zheng Liuzhang.

"Oh, Sister. Do you see this? This brush."

"Huh? Why? Is it good? If it's good, take it quietly."

"No, Sister. It looks fancy, but it's just a fake made of dog hair. Even if you don't have an eye for art, you wouldn't buy something like this. The owner of such a terrible brush must be an ignorant nouveau riche with no culture. You call this trash a brush?"

After saying that, Zhuge Lixian suddenly clenched his fist.

The large hand was covered in bulging veins, and with a crack, he demonstrated his skill of turning the brush into something else.

Then he threw it carelessly, and the broken brush lay scattered at the foot of Zheng Liuzhang.

Qing couldn't help but admire him.

\textit{Wow, Zhuge is quite skilled.}

\textit{As expected, those who are smart are good at psychological warfare.}

"You…! What…!"

Zheng Liuzhang's body was shaking.

His clenched fists were also shaking.

It looked like he was about to strike.

As if to calm him down, Qing spoke in a gentle voice to the trembling Zheng Liuzhang.

"Hey, Young Master Zheng. Is breakfast ready yet? Ah, I'm hungry in the morning, so let's have a chicken for each person. And a jug of wine, too. What would you like to eat, everyone? I'll have sticky rice."

"I'll have porridge."

"Ah, I'll have pancakes. With japchae."

"Sister, I like Yunnan rice noodles."

Then, all four of them looked in one direction.

"…"

"…" "…" "…" "…"

"…"

"…" "…" "…" "…"

There was a moment of silence. Then.

"…Hundun\footnote{dumpling soup}."

As was commonly said in Qing's hometown, in a world of one-eyed people, those with two eyes were simply the disabled.

Peng Daesan gritted his teeth as if he wanted to chew up all the dumplings, forcing out a reply.

"Well, did you hear that? Young Master, hurry up and get it ready. I'm hungry."

Zheng Liu's heart was racing.

The customer's attitude toward the owner was terrible from the start, but now he was treating him like a waiter.

On top of that, sticky rice, rice porridge, rice cakes, rice noodles, and dumpling soup?

If they were going to eat for free, they should at least order the same thing. How was he supposed to prepare five different meals?

But he endured.

\textit{Think of the greater good.}

\textit{It would not be good to get into a pointless argument, especially if it involves that woman from the Tang family. If an argument breaks out, it could interfere with the greater good.}

\textit{The reason why Poison Demon is going to the trouble of secretly handling this through a ten-sided ambush is because he is worried that Zhongyuan people will find out.}

\textit{Therefore, I have to let it go…}

"Um, you guests look very tired and hungry, but my servants are away, so it will be a little difficult, but I will do my best to serve you."

They were tired and hungry, so they might be rude, but he would give them food, so they should just eat whatever he gave them.

In fact, anyone could see that Zheng Liuzhang's words and actions were those of a noble man.

If Shakyamuni had seen this, he would have smiled mysteriously, saying, 'That is the mind of Buddha'.

Confucius would have admired this, saying that it was the way of a gentleman to respond to rudeness with kindness and make the other person feel ashamed.

Unfortunately, however, the person present there now was neither Buddha nor Confucius, but Ximen Qing.

"Wow, Young Master. Are you a eunuch?"

"What do you mean?"

"No, I just couldn't believe that a man would act so cowardly without balls. Don't you have any pride? How can you do such a despicable thing and not say a single word in your defense?"

Zheng Liu's eyes widened, and he blinked repeatedly.

Faced with such direct insults, he was momentarily confused as to what he had just heard.

But that moment passed quickly.

"Just because someone is rude, it doesn't mean you have to respond in kind. In fact, if you respond to rudeness with rudeness, won't that just leave you with nothing but hatred for each other?"

"No, think about it. No matter what, doesn't that make no sense? If you act so submissive, won't it look suspicious?"

Qing narrowed her eyes and continued.

"It's as if you're hiding something."

Zheng Liuzhang swallowed hard.

"…If you show kindness and lead by example, they will be ashamed and correct themselves. Even Confucius said so."

"Oh. Confucius. Confucius is good. But."

Qing put her feet down, then bent over, leaning her elbows on the table and resting her chin on her hands.

But because Tang Lan-Ah was sitting on top of her thigh, she just lowered her legs and put her chin upwards.

"You hid the cure for a contagious disease that iss all the rage in order to benefit yourself, and you hired swindlers to gather people for human trafficking, and now you're talking about virtue? That makes you look even more suspicious."

"I already explained that it was to gather miners, and we pay them a fair wage…"

Qing pretended to listen and glanced left and right.

Then there was a loud crack as the wooden floor shattered.

Two men on either side of Zheng Liuzhang lunged forward, grabbed the arms of Zheng Liu, bent them backward, and kicked the ankles, slamming his head into the floor.

"Ugh. Ugh…"

Qing put down Tang Lan-Ah, stood up, and walked away, deliberately making loud footsteps.

Then she crouched down next to Zheng Liuzhang with a disrespectful attitude.

"Hey. I'm the one who set fire to the mine. Me. Ta-daa. Surprising fact."

"What? What?"

"No, underground… I'm getting anxious again. I feel like I'm going to throw up, so stop pretending to be a good person. Blood Cult, right?"

"I don't understand what you're talking about. I think there's been a misunderstanding."

"What do you think happened to the Blood Cult members who lived in front of the mine? They were all thrown into the basement alive, right? But I didn't kill them, so thanks to the light from the moon, they can see, the air circulates, they have water to drink, and there's plenty of food, right?"

"What are you talking about?"

"People are the staple food of your Blood Cult. First, they'll eat the corpses of poor people from Zhongyuan, and then they'll draw lots to decide who eats who, right? Or maybe they'll eat the weak ones first. One by one, they'll eat each other. Wait, they'll eat each other? Isn't that pretty much what you Blood Cult people usually do?"

Qing's voice dripped with cold malice.

Zheng Liuzhang's head, who had been stiff with fear, suddenly slumped forward, his head hitting the ground with a thud.
