\chapter{Let's Achieve Slaughter (3)}

"You killed them all? They are just ordinary people who knew nothing about martial arts. They are just poor people who are happy to have three meals a day and a roof over their heads, and they had finally begun to live like human beings…"

Zheng Liuzhang 's voice trembled slightly.

His forehead was pressed against the floor, so it was impossible to see his expression.

However, from his trembling, moist voice, it was easy to guess how he felt.

However, Qing's eyebrows twitched.

Ordinary people do not make poison from human corpses.

Not even to the extent of creating the corpses themselves.

\textit{What do you mean living like human being?}

\textit{You made them kill and eat other humans to survive, and now you think you're some kind of guardian of the people?}

\textit{But not yet.}

\textit{This isn't the time to debate who's right or wrong. This is a slaughterhouse for executing the Blood Cult.}

"Human? Is there any human in Blood Cult? They're nothing but vermin. That's why the only good Blood Cult members in the world are the dead ones. I have turned them into good people, so those Blood Cult vermin must be thanking me in hell, right? Of course, they're being tortured in the eight levels of hell because of their sins, but I prevented them from committing even greater sins, didn't I?"

"Crimes? What right do you have to say that? You are the criminals. You Zhongyuan people are the worst murderers."

"What? You vermin dare to speak?"

"So you want us to just die quietly? Do you have any idea how our people live? No, that's not even living. We're being raised like livestock, no, even livestock wouldn't be treated this way."

"Because you're not even worth being called livestock?"

"Do you even know what you Zhongyuan people do to us? Just because we were descendants of traitors, you pushed us into the most barren land. We can't even farm, and you built embankments to block the rivers, and if we try to leave to survive, you stab us with swords and spears…"

"No, I don't care about your situation at all."

"Even when you Zhongyuan people invade us, claiming to be fighting for justice, our people were beaten and forced to cower. Human trafficking? You Zhongyuan people always take our people as slaves. The only reason you don't exterminate us is so that we will bear children to be your slaves. Even animals are not treated this way."

The villages in Zhongyuan were mainly composed of families with the same surname, so there were villages where the descendants of traitors live, which were called traitor villages.

How were traitors treated in Zhongyuan?

Of course, Qing couldn't believe what she was hearing.

This was because, as far as Qing knew, what Zheng Liuzhang was talking about happened a long time ago.

It was now nearly three hundred years since the founding of the current dynasty.

It was impossible to devote military resources to blockading a traitor village for over a hundred years, nor should it have been done. If the manpower assigned to the blockade were used for farming, how much grain could be produced?

Therefore, they either fled in groups to settle in the deep mountains,

Or they could change their surnames and settle in Zhongyuan, but since it was not a country with a resident registration system like Qing's hometown, as long as they were careful with what they said, there was no way they would be found out.

Nevertheless, the Blood Cult still claimed that they were being persecuted for the sins of their ancestors, whom they do not even know.

This was because it was the way the Blood Cult maintained its power.

The Blood Cult find hidden villages of traitors, sealed them off by posing as government soldiers or martial artists, and slowly killed the villagers through all kinds of exploitation.

However, one day, a group of warriors carrying the Blood Cult's flag would storm into those vilaages, and after a fierce battle, the flag of the Blood Cult was raised.

The Blood Cult then claimed to have rescued their fellow countrymen.

And yet, even now, there were still fellow countrymen suffering throughout the land.

Let us join forces and drive out the oppressors of Zhongyuan with the power of our fellow countrymen!

As time passes, the oppressors of Zhongyuan (who were actually members of the Blood Cult in disguise) realized the ideals of the rebel village and appear to treat the villagers like animals.

Once the Blood Cult has established itself as the religion of the village, this oppression only served to fuel the villagers' anger and strengthen their devotion to the cult.

What if the Blood Cult has not established itself in the village?

Then you will enjoy the periodic liberation of the village from the Blood Cult and the reoccupation of the village by the oppressors of Zhongyuan until the Blood Cult takes root.

So, what was the miserable and terrible life of their compatriots that the Blood Cult followers talk about?

It was nothing more than the terrible brainwashing that the Blood Cult itself used to abuse and raise its followers.

'Therefore, Disciple, the Blood Cult was like fleas or rats. If you don't crush them as soon as you find them, they will multiply in an instant. So, Disciple, remember this well. You may pity them, but you must never show them mercy.'

Those were the teachings of Ximen Surin.

'Keep in mind that if you spare them because you feel sorry for them, even those who would not have become members of the Blood Cult will be driven into the abyss of their terrible evil deeds.'

Ximen Surin had emphasized this point strongly.

Zhongyuan's Wulin had already experienced the rampage of the Blood Cult many times, so they knew very well why these terrible scum of the earth were not exterminated, or rather, why they could not be exterminated.

Therefore, Qing's eyes narrowed.

\textit{Does this guy really believes that?}

\textit{He has no martial arts skills, so he must be a genuine Blood Cult member who was picked up from a Blood Cult village and used as a disposable pawn.}

\textit{No, that can't be.}

\textit{If he is responsible for running a poison factory, he should have a high position within the Blood Cult, so he would know the truth about the Blood Cult.}

\textit{And before his true identity was revealed, he was acting so natural, not changing his expression, pretending to be a moral merchant while committing fraud.}

And Qing came to a conclusion.

\textit{Kid, you're stalling, aren't you?}

\textit{In the first place, isn't it too unnatural to come out with this story at this moment?}

\textit{After all that provocation, and even after setting fire to the mine, how can you sit there telling a sob story without even a single curse word?}

\textit{If it were me, I would have yelled 'I'll kill you! I'l skin you alive, rub you with salt, pickle you, and fed your meat to your parents'.}

\textit{But, um, what is this? Is this okay?}

In fact, there was no reason for Qing to completely subdued Zheng Liuzhang and then poured fuel on the fire.

She could have just smashed and stabbed him here and there to make him suffer as much as possible.

But even so, she tried hard to pour fuel on the fire and turned him inside out. Qing's original plan was to provoke him into saying something stupid after making him really angry.

\textit{But what about this?}

\textit{I don't know who he's waiting for, but if I throw a little bait when he voulnatrily talk on his own, maybe he'll bite?}

"So, you feel wronged? You had no choice because Zhongyuan people persecuted you? In order to survive, you spread disease and pretended to sell medicine to lure innocent people to their deaths?"

"I won't make excuses for that. But we are only trying to survive. And compared to what you have done…"

\textit{I threw out a little bait, and it is a big catch.}

\textit{These bastards spread disease and sold medicine, why do they do such despicable things? As expected, the only good Blood Cult members are the dead ones.}

Qing's eyes flashed with a sinister light.

The first to react was Tang Lan-Ah.

"Uh, wait, what did he just say?"

"Ha. Why didn't I think of that sooner?"

"Sister. If I heard correctly…"

"It's strange. Langzhong Daren said that the disease is not contagious, but people keep getting sick. And what? Smallpox? He also said that there are no pure bloodlines these days, so how can the disease discriminate between people? And it is the Blood Cult who are tampering with the medicine? I should have realized it sooner."

Zheng Liuzhang's eyes widened.

He seemed to be a smart guy, but now he realized that he had said something he shouldn't have.

"Wait, you said we spread the disease? That's a misunderstanding!"

Zheng Liuzhang tried to add something, but he let out a scream that sounded like a howl.

Of course, since Qing's index finger shot into his eye socket.

All the way in, two knuckles deep.

In an instant, it felt like a bolt of lightning struck from her fingertips, sending a thrill down her spine!

\textit{Yes, yes, that's it, yes.}

"Ugh. That's it."

Qing trembled and twisted her fingers.

The milky eye juice left traces on the floor.

Zheng Liuzhang was shaking, swaying, and trembling.

That was all Zheng Liuzhang could do, as he was pinned down by two masters.

After a moment.

Zheng Liu, drenched in sweat, slumped down.

"Ugh, ugh. Ugh."

"Hey, you're pretending to play along, so people think you're easy to deal with, huh? You're wasting time with nonsense that even a dog wouldn't believe. Huh? Do dogs believe nonsense? Anyway, why are you wasting time?"

\textit{I wonder if my bad luck is going to strike again and some master will show up.}

Qing hid her true feelings and tapped Zheng Liuzhang on his head, grumbling.

"Those guys who went out to extinguish the fire aren't even worth mentioning. Why, do you have a master of Harmony Realm hiding somewhere? Will they come if you stall for time?"

"I'm not stalling for time—"

That was the moment.

"Excuse me, Young Master…? I found this in the kitchen. It looks like a letter from Yoo-ryun…"

A frail voice interrupted, and the group (plus the one-eyed man) turned their heads in unison.

Zheng Liuzhang, who had been waiting expectantly, showed a spark of excitement in his remaining eye, but it was only for a moment before his face contorted.

It was just like Zheng Liuzhang's usual quarrel.

The servant, who had heard the guests gathered and screamed, thought that the Young Master was playing some kind of prank, but when they saw the face of their Young Master, they gasped in surprise and-

Deeng!

With the sound of a temple bell, the servant's head was blown to pieces, scattering its contents in all directions.

The headless body collapsed.

Qing let out a sigh.

\textit{Surely, killing Blood Cult members who knew nothing is not a pleasant feeling.}

Qing went outside and grabbed the letter from the corpse's hand.

She unfolded it, skimmed through the contents, and furrowed her brow.

\textit{What is this?}

Then she chuckled.

Qing reads the letter aloud.

\begin{quote}
	Young Master, if you are reading this letter, congratulations, it means that you have avoided a great danger by pure luck.
	
	However, I can no longer protect you. Because Yoo-ryun must now disappear. 
	
	So please take care of yourself.
	
	Of course, don't trust those worthless rascals of the Zheng family. I can wipe them all out by myself. I can wipe them all out with just one finger. You know I'm not joking, right?"
\end{quote}

Jeong Ryu's expression suddenly contorts.

It seemed that the person he had been waiting for was the owner of this letter, Yoo Ryun.

Qing finished reading the letter.

\begin{quote}
	My contract with the Blood Cult is over! Yoo Ryun is free! Wait for me, world! This free Yoo Ryun is coming!
\end{quote}

\textit{I don't know who this Yoo Ryun is, but they seems like a rather pleasant person.}

\textit{Since they are the person Zheng Liuzhang was waiting for, they must be quite skilled, but if it was a contract, were they a wanderer?}

In any case, Zheng Liu's expression was quite something to see.

Anger, shock, betrayal, confusion, and denial of reality were all mixed together, and the deep fear that he had never shown before was finally revealed on his face.
