\chapter{I Don't Like This Kind of Trend (7)}

Peng Daesan felt uneasy.

Why was he uneasy?

To Peng Daesan, women were objects of contempt.

They were nothing but leeches who imposed their will based solely on appearances.

If Qing had heard this, she would have scoffed, saying, 'What, do you think all women in the world only care about looks?'

But to Peng Daesan, that was exactly how it was.

Because, to him, the persistent and shameless followers, the obsessive few, represented all women.

After all, the vast majority of women who either had no interest in him or simply admired his looks and moved on were people whose existence Peng Daesan couldn't even acknowledge.

If you traveled to another country and every single person you met was wearing torn clothes, wouldn't you naturally assume that people in that country just wore torn clothes?

So Peng Daesan felt uneasy.

How could he not, when he had to hide his true feelings and flatter someone he despised?

And that damned Qing.

How could she asked him to do something so humiliating, knowing full well how he felt?

Even if it was for the sake of chivalry, it was too much.

The more he thought about it, the more furious Peng Daesan became.

``Come on, come on, cheer up. What's with that sour face? Let's go.''

``Ha.''

``Come on. Hurry up.''

Qing's nagging was unbearably annoying.

``Excuse me? I'd like to ask something.''

At that, the door of the house cautiously opened.

The tired face of a woman peeked out for a moment—

``Gasp.''

And then the door slammed shut again.

``Looks like it's not working. Let's go back.''

Just as Peng Daesan was about to turn around—

``Wait, please wait a moment!''

A desperate voice called out.

After a short while, the door opened again.

``Greetings, Great Hero. How may I assist you?''

The woman, who had neatly combed her hair and dressed in clean, albeit faded, clothes, appeared with a composed demeanor.

Qing tilted her head.

\textit{Hmm, she even put on makeup in that short time.}

\textit{It's over, it's over.}

Qing gave Peng Daesan a look.

Even though the look was hidden behind the veil, the slight turn of the head was enough to convey the message.

Peng Daesan's brow furrowed, and he stared silently, unable to speak, before finally uttering a single word.

``Hmm.''

It was an uncomfortable, low-frequency sound.

The woman suddenly covered her mouth.

She had been through a lot.

Taking care of her parents who had fallen ill with the plague, with no sign of recovery and no end to the quarantine in sight.

Even the food provided by the kind doctor was being taken by the terrifying swordsmen of the Unorthodox sect, leaving almost nothing for her sick parents. She was so hungry and exhausted that she could barely stand.

When people were pushed to their limits, they inevitably seek salvation from a divine being.

And now, the legendary Great Hero, radiating an aura of brilliance, had appeared before her. The relief and sorrow!

And as the stories often go, the overwhelming gratitude—if she could repay this debt in her lifetime, the woman's mind was filled with visions of a large, happy family, with six children, grandchildren, and great-grandchildren, all laughing together for no reason…

``Sniff, Great Hero…!''

Suddenly, with reddened eyes, the woman rushed forward!

Peng Daesan's expression froze as the woman fearlessly threw herself into his arms.

\textit{Ah, how could you be so warm and soft, your caressing hand so cool…}

\textit{Soft? Cool?}

The woman looked up, and the sharp line of a woman's jaw peeked out from beneath the veil.

Even from this unflattering angle, her beauty was undeniable.

And her gentle voice.

``Ah, it seems you've been through a lot.''

``Uh, who, are you?''

``It's alright. When people were overwhelmed, they sometimes unconsciously seek comfort from someone.''

``No, why are you comforting me? Let go.''

``Ah, no matter how hard it is, you shouldn't throw yourself at a stranger. You never know what people might say, it's scary.''

``No, why are you worried about that—''

``It's alright. You must have been through so much,''

``Wait, let go. Ugh.''

``Ah, even adults need comfort sometimes. If you're going through something difficult, just let it all out.''

``No, what strength-''

``Come on, who's bothering you? It's alright, just tell me. I'll take care of them.''

The woman struggled to break free, but Qing was a master of the Flower Realm.

Even if she wasn't, her strength alone was beyond human limits, so no matter how hard the woman tried, there was no way to escape.

For a while, she squirmed and wriggled.

It wasn't a fight or an argument, just squirming, which would only make sense if Qing was being shaken.

The woman was stuck like a boulder.

Finally, she exhausted.

The woman slumped in Qing's arms.

Qing smiled and gently patted her head.

``Come on, if you're going through something, just let it all out. Keeping it inside will only make you sick. Don't overthink it, how have things been lately?''

The woman poured out everything.

At first, she hesitated, unable to hide her discomfort, but as she spoke about her parents who had suddenly fallen ill and her brother who had left to earn money for medicine, she finally broke down and let it all out.

And she also spoke of the atrocities committed by the Jangyun Sect.

They took half of the food rations.

Fortunately, thanks to Langzhong Daren increasing the amount of food distributed, even after taking half, there was still enough to avoid starvation.

\textit{Those bastards, how dare they deceive me? They're all dead.}

\textit{And I didn't even say I'd kill them all.}

\textit{I just wanted to cripple them, but now with the added crime of deceit, they're all dead.}

And so, back to the Jangyun Sect's gate.

Bang bang bang!

The sound of knocking was deafening.

Qing was like a human battering ram. With just a push, the gate of this estate would be shattered in one blow.

But the loud noise meant that she still showed some mercy.

Why?

Was it because Qing's burning carpenter's soul couldn't bear to destroy something she had worked on with her own hands?

``Who's there!''

``What's going on!''

Of course, that couldn't be the case.

Qing's knocking was a kind of polite warning.

'We're coming in, so gather quickly.'

For a while, the rhythmic banging continued, filling the air with a strangely festive beat.

After what felt like an eternity of noise that could wake the entire neighborhood, Qing finally put her full strength into it.

Bang! The gate shattered into pieces.

Under the plaque, Qing and their group confidently stepped forward.

They had given plenty of time by knocking, so the courtyard was now surrounded by armed Jangyun Sect disciples.

In the center, the burly, menacing sect leader, Chosam Il, roared.

``What is the meaning of this! Even if we're in seclusion, do you think we'll tolerate such behavior!''

``You like seclusion, huh? Thieves who prey on the sick, what kind of seclusion is that! I've heard everything, so what, you swear on your parents' names? You lie on your parents' names? What kind of son of a bitch does that!''

``What, what!''

Chosam Il's face turned bright red.

In Zhongyuan, filial piety was of utmost importance.

Thus, calling someone a 'son of a bitch'\footnote{胡奴子息; Hunu Zhixi; lit. 'barbarian's descendant'; implying one's mother was raped by barbarian and then gave birth to them} was one of the most serious insults one could hurl.

Of course, Chosam Il, who had boldly lied on his parents' names, was indeed a son of a bitch.

But even if it was true, openly shouting it in front of his subordinates was a different matter.

``You, you bitch, I was going to let this slide, but it seems words won't work!''

``Oh, you won't use words? How scary. Wow, you're so scary. But wait, everyone, look here. Twinkle twinkle.''

Qing raised her sword, scattering starlight.

Sword Force. The cold blade that made one's heart ache just by looking at it.

It was a ridiculous act, but Chosam Il couldn't laugh.

\textit{Sword Force? This bitch is a Trasncendent Realm Master?}

Qing's antics didn't stop there.

``Is that all? Twinkle twinkle one!''

``Twinkle twinkle two!''

Jian Buxi, with her uniquely naive yet seductive, innocent yet lascivious smile, raised her hand.

A deep pink, alluring peach-colored starlight.

Now there were two starlights.

``Twinkle twinkle three.''

Wait, three.

On the other side, Xue Iri, holding an ice sword, emitted a pure white Sword Fura.

Qing's head turned sharply toward Peng Daesan.

Peng Daesan's hat swayed slightly from side to side.

'No.'

Qing's veil also swayed.

'Fine.'

A moment later, with a click of the tongue, a fourth starlight, wrapped in a thin blade, bloomed.

Chosam Il blinked.

Then, like an old man with blurry vision, he leaned forward, squinting and rubbing his eyes.

But the four-colored light sources emitting their own Sword Force didn't disappear.

Chosam Il's heart sank.

Unlike in the past, Transcendent Realm martial artists were now quite common.

Due to the overall rise in martial arts, even small cities usually had at least one Transcendent Realm master who could emit Sword Force.

Larger cities might have three or four.

And how many cities were there in Zhongyuan?

But while Transcendent Realm martial artists were common across Zhongyuan, it was unlikely for a small Unorthodox sect to have one.

Of course, Realms didn't guarantee victory, and with the full force of the sect, they might be able to do something.

But in other words, to face one Transcendent Realm martial artist, the entire sect's strength would have to be concentrated.

But four?

This was just too much.

Chosam Il's back was drenched in sweat.

``Uh, well… it seems there's been some misunderstanding. Could we perhaps resolve this through conversation…?''

``Didn't you say words wouldn't work?''

``Misunderstanding, it's a misunderstanding. I was just trying to speak…''

Chosam Il became polite.

After all, there weren't many martial artists who wouldn't be polite in front of four Transcendent Realm martial artists.

Even if he was also a Transcendent Realm martial artist, he'd rather use words over swords in front of overwhelming numbers.

``Misunderstanding? You said it well. What misunderstanding? You're in seclusion, huh? Too ashamed to continue, so you decided to stop?''

``That's! I clearly ordered it to stop, but there must be those who disobeyed my orders. I swear on my honor, I will investigate thoroughly and punish them severely—''

``Ah. So it's individual misconduct? The sect leader ordered them to stop, but the subordinates acted on their own?''

``Y-yes!''

Qing tilted their head.

``Why is that individual misconduct? If a disciple commits a crime, the sect leader should be held accountable. Isn't that why there's a sect leader? What, is the sect leader just there to laze around and give orders?''

``T-then what should I do—''

``First, cut the tendons in the legs.''

Qing cut off Chosam Il's words.

Then added one more thing.

``And you dared to lie to me? For the crime of deceit, I'll also destroy your dantian.''
