\chapter{I Don't Like This Kind of Trend (1)}

Yunnan Province, Qujing County.

Qujing County is, in a way, a gateway city.

Qing arrived here after continuously changing carriages from Changsha in Hunan, which means there were well-maintained official roads suitable for carriages.

The roads that carriages travel on were also good for walking, making it the most convenient and safest route to reach Yunnan.

Thus, Qujing was the first city travelers reach when entering Yunnan, whether they were merchants heading to Yunnan or tourists flocking to see the famous Yunnan scenery.

They had departed from the academy around mid-September.

And now, just a few days before the end of October, they arrived in Qujing, marking a journey of about a month and ten days.

But they were still far from their destination!

There were still fifteen hundred li to go to reach the Diancang Sect…

However, since there was no urgent business, it didn't particularly matter.

During the journey, they frequently encountered people on the official roads, which made them realize that quite a few travelers were heading to Yunnan.

But upon arriving in Qujing and trying to secure lodging at an inn, they found that both here and there were fully booked, with no vacancies.

Of course, when they said ``fully booked,'' it referred only to the best rooms in the inn. If they had to stay in a cheap room, they would rather lower the standard of the inn but still aim for the best room available.

Why? Because they had money.

Their pockets were full.

Qing had now fully become one of the privileged, well-fed pigs of the Zhongyuan' martial world!

Thus, after settling into a high-class inn (not the top-tier one), they came down for a meal and found the entire first floor of the spacious inn packed with guests.

``Wow, it's crowded. Is there really that much to see in Yunnan? Maybe we should visit the Diancang Sect and then take a tour around. Who knows when we'll come back to Yunnan again.''

``Indeed, Yunnan was known for its scenic beauty. Just walking around, you'll find breathtaking views everywhere. But, sister, this isn't a good sign.''

``Huh? What do you mean? The crowd?''

``No matter how much this city was called the gateway to a province, it's absolutely not normal for it to be this crowded without any special event.''

``Hmm. Is that so?''

``Just look at the food here. Doesn't it resemble Guizhou cuisine?''

``Ah. What's going on? Is the chef from Guizhou?''

``I've heard that Yunnan was somewhat like this. It tends to resemble the nearby regions.''

Yunnan borders Guizhou to the east, Burma and Tibet to the west, Lancang and Vietnam to the south, and Sichuan to the north.

The cultures of these different regions converge here, but instead of blending, they remain distinct, each resembling the nearby areas.

This was why Qujing, the first city you encounter in Yunnan, doesn't differ much from the customs of Guizhou.

The food was strongly sour, which can be described as tangy in a good way or simply sour in a bad way. People from Guizhou might wonder why so much vinegar was added.

Because of this, Xue Yi-ri was feeling down.

Even though Guizhou cuisine was known for its spicy and sour soups, Xue Yi-ri, a soup enthusiast, finds it far from her taste.

In Guiyang, the capital of Guizhou, there's a spicy trend, but the result was a spicy and sour soup.

However, apart from that, the traditional Guizhou soup was fundamentally sour.

``There were no famous landmarks nearby, and this isn't a city that should be this crowded, sister.''

``Well, there might be some event happening, right? Maybe a big local festival was about to take place. We can just ask. Hey, waiter!''

While Qing was calling for the waiter, she could hear others calling for waiters too, and the waiter's usual smiling face stiffened slightly.

But only for a moment.

The waiter, holding a thin slice of silver coin, became extremely polite.

During quiet times, it's fine to just ask, but during busy times like this, it's customary in the Zhongyuan to tip generously if you want to hold their attention.

``Hehe, what would you like to ask, miss?''

``It's just that there were so many people. Is there some festival or event happening soon?''

``Oh, miss. It's not that. Haven't you heard? There's a strange disease spreading in Chuncheng.''

``Ah. A strange disease.''

A strange disease, an unusual illness. ``Unusual'' implies an unknown, mysterious disease, and ``spreading'' means it's contagious.

So, it's not a festival but a funeral.

In an instant, Qing, who had turned into a clueless tourist, awkwardly scratches the back of her head.

``In Chuncheng, they've sealed off the area and quarantined the sick, so they say it's under control. But the disease was scary, so some travelers were checking the situation, and there's a lot of commotion about quarantining the sick. They say it takes two days just to get into Chuncheng. Unless you're a merchant who needs to pass through the Tea Horse Road, even if Chuncheng was warm, it's not worth staying up all night for.''

Chuncheng was written with the character for ``spring.''

It's a nickname for Kunming, the capital of Yunnan Province, known for its spring-like weather year-round. Kunming's climate was said to be like spring all year long, with no distinct seasons.

But that's not entirely true.

The Zhongyuan folks tend to exaggerate when talking about their hometowns, so it's more of a spring-like feeling, and the temperature can vary greatly, making autumn nights quite cold.

``Hmm, a strange disease, huh? What should we do? Should we avoid Kunming and take a detour?''

``No. If the disease has spread to the capital of a province, how bad must it be in the rural areas? Most villages don't even have physicians.''

Tang Lan-Ah, for once, makes a smart remark.

After all, Tang Lan-Ah was a physician and a member of one of the Zhongyuan' top medical expert groups.

Hmm. Then there's no other choice.

Qing isn't afraid of diseases or plagues.

Her strange constitution allows her to consume poison without issue, feeling only a spicy, tingling sensation in her stomach.

But her friends aren't like that.

Plus, there's still the young Ciyu.

Hmm, it seems there's no choice but to send them back and go alone.

Qing's eyebrows droop at the ends.

``Hey, guys—''

In an instant, everyone except Qing and Ciyu exchanges glances.

It's obvious what she's about to say: ``You guys go back and live safely, I'll break through the plague and head to the Diancang Sect.''

Even if they suggest going back together, she definitely won't listen.

Tang Lan-Ah quickly cuts Qing off.

``But look, there were so many people here. If it were a real epidemic, people wouldn't even come near this area, right?''

``Huh? So?''

``From what I can see, it's either a type of disease that doesn't spread unless you directly touch the infected area, or the claim that Kunming has quarantined the sick and sealed off the area isn't entirely true. In that case, rather than taking a detour, it's better to pass through Kunming and quickly head to Dali.''

``Hmm.''

``Sister Dang was right, sister.''

Peng Daishan agrees in a low voice, and Zhuge Yi-hyeon chimes in.

Qing falls into deep thought.

What's this? Is Tang Lan-Ah really the older sister to Zhuge Yi-hyeon?

For now, it seems they should head to Kunming.

If it were a real disaster, they would have sealed the city gates and prevented anyone from entering. But since they're just conducting strict inspections, it doesn't seem that serious.

If they go and find out it's not a big deal, they can send the others back and go alone.

``Qing, let's eat and then go together.''

``Huh? It's almost night. Aren't we going to sleep?''

``No, I'm not saying we should leave now. Since there's a disease spreading, we should avoid staying in villages. We should stock up on supplies and be careful on the road. I'll also prepare some basic medicinal herbs.''

Tang Lan-Ah's behavior was quite unfamiliar.

Usually, she's like a chihuahua, trembling with anger and growling, but now she's acting like a seasoned physician.

``Qing and I will go check out the medicinal herbs. You guys go buy enough supplies for the night. Qing, you said you've read some medical books, right? I'll teach you how to identify herbs. The herb sellers were really good at sizing people up. If you don't know, you'll just get scammed.''

Of course, Tang Lan-Ah didn't forget to take advantage of the situation to satisfy her own interests, truly living up to her reputation as a wicked woman of the Dang Clan.

The City of Flowers, Kunming.

Kunming was known as the ``Spring City'' due to its mild climate year-round, surrounded by gentle mountains on three sides and a large lake on the other, ensuring abundant water supply.

Thanks to this, flowers bloom all year round, making it beautiful, and besides being called the Spring City, it's also known as the Flower City.

When Zhongyuan people were asked to name the most beautiful city in the world, where do they point?

Guilin! Guilin was undoubtedly the most beautiful.

Kunming was only third.

But being third was still a great achievement.

How many cities in the Zhongyuan were famous for their beauty?

And more importantly, it's necessary to understand the logic behind how Zhongyuan people rank these cities.

When ranking in any category, the first place was a city that everyone would nod in agreement with, a proven city. The second place was their hometown.

For example, if asked to name the most culturally advanced city, the first place would be Hangzhou, the second would be the capital of their home province, and the third would be Luoyang or Beijing.

Thus, being ranked third in the category of beautiful cities means that, after removing the inflated hometown bias, Kunming was actually second in reality.

Anyway, thus, Kunming!

But they were still far, far away!

There were still nine hundred li to go to reach the Diancang Sect…

Just how remote was this place?

Although they had been camping along the way, renting the most expensive carriage and sleeping under a roof was much better than staying in a cheap inn.

At least there were no bedbugs or fleas, and the uneven, hard beds with protruding straw didn't prick their skin.

Of course, Peng Daishan and Zhuge Yi-hyeon, who had to sleep outside due to being men, might have a different opinion.

But this was how the privileged class of the Zhongyuan travels!

Whether in the Zhongyuan or Qing's hometown, the principle remains the same: if you have enough gold, you can avoid much of the hardship.

As the waiter had said, from the spot where the city gate could be seen in the distance, a long line of people was waiting to enter Kunming.

This was because Kunming was also an important stronghold defending the Zhongyuan from foreign threats to the west.

With mountains behind and a lake in front, it's a natural barrier, making it much faster to pass through Kunming even if it takes three days of waiting.

Despite the disease spreading, why were so many people, especially merchants with their carriages, eagerly waiting to enter?

Because beyond Kunming lies the Tea Horse Road, the production area of Yunnan tea, the best tea in the Zhongyuan.

It's said jokingly that if you have enough time, you can travel to Yunnan for leisure. If you buy Yunnan tea and sell it back home, you can earn back all the travel expenses.

Thus, for merchants dealing in Yunnan tea, no matter if there's a disease or war, the carriages must keep moving.

That's the life of a merchant.

Because of this, only Qing's group suffered from the long wait.

They had thought the waiter's claim that it would take two days to enter Kunming was an exaggeration typical of the Zhongyuan.

But it turned out to be a straightforward fact.

The processing was just that slow.

Physicians and nurses checked for symptoms, which took forever, and the guards, overworked and stressed, were extremely strict, asking about every item they carried, where they came from, and why they were here, to the point of being infuriating.

Moreover, the city gates closed at sunset!

Then you just have to wait until morning. What else can you do?

``Are you tourists? Tourists at this time? Suspicious. The Diancang Sect? Heading to Dali? Why? Personal business? Is there anyone who can vouch for your purpose? Hmm. Suspicious. We'll search your luggage. Unload everything. The cargo on the carriage too.''

The gate guard was being difficult.

It almost seemed like he was deliberately causing trouble to solicit bribes, but Zhuge Yi-hyeon remained unusually quiet.

Zhuge Yi-hyeon, who was usually smooth and good at handling situations, would have stepped forward with a smile, saying, 'Officers, you've worked hard', and subtly slipped them some silver.

But since he remained silent, it must not be the right time for such tactics.

\textit{Hmm. No wonder the line takes two days…}

However, the guard's high-handed and unfriendly attitude didn't last long.

The guard frowned as he fiddled with the silk pouch Qing handed over.

``What's this? An identification tag? Why is there another one here? What's the first one you submitted? Why do you have two—''

``Ah, that's—''

``Gasp.''

The gate guard, who had roughly opened the silk pouch to inspect its contents, froze on the spot.

Inside was an Imperial Inspector's token.

\begin{lstlisting}
The chapter title is a reference to webtoon 'I don't like this kind of hero'.
\end{lstlisting}
