\chapter{I Don't Like This Kind of Trend (8)}

What does the dantian mean to a martial artist?

Every martial artist in the world would say this.

They would rather die as a martial artist than live as a pitiful commoner who has lost their dantian.

``You, cruel one, just kill me!''

``Oh, really? Then it's easier for me. Alright, those who want to die, stand on the right. Those who want to live, stand on the left. I'll count to ten. One! Two—''

At that moment.

``Stop!''

A voice filled with determination cuts off Qing's counting.

Qing looked up and saw a man of a rather high position, judging by his expensive silk clothes.

Qing didn't know, and frankly didn't care, but this man was the general manager of the Jangyun Sect.

Seeing the middle-aged man's solemn expression, Qing nodded.

``Indeed, as a martial artist, you can't give up without a fight. Is that it? Then—''

``No, no, that's not it. You need to clarify which left you're referring to. Is it the left from your perspective, or the left from ours?''

Every martial artist in the world would say they'd rather die than lose their dantian, but when it comes to actually facing death, very few would choose it.

It was a simple truth.

In Qing's homeland, if you asked someone publicly whether they'd give up their dreams for a million dollars, ninety-nine out of a hundred would say they wouldn't give up their dreams for just a million.

Because it's not like they're actually going to get a million dollars, and if they answered honestly, they'd look like someone who sold their dreams for money.

But if you actually offered them a million dollars, who would refuse?

``Ah. Hmm, the left from my perspective, so that would be your right, right?''

``Ah. I see. Ahem, we should definitely clarify this…''

The general manager was the first to move to the right.

Seeing this, the disciples followed suit, quickly gathering on the right.

Chosam Il was greatly bewildered.

What on earth is this atmosphere?

If the entire sect had united and charged, he might have been able to escape in the chaos.

But now, the situation has became absurd and the atmosphere has completely shifted.

Even if he tried to rally them for a desperate fight now, who would dare draw their swords and oppose?

``What about you, the boss? Are you neutral? Or do you want to die halfway? Should I split you in half?''

``Well, even so, the dantian is a bit… why the crime of lying is greater than our misdeeds…''

``Ah, of course, hmm. Right. You'll probably understand soon?''

He didn't know what it means, but it's clear that Qing intended to destroy his dantian and cripple him.

Chosam Il kneeled on the ground.

``Ah, Great Hero, I have committed a grave sin. If you spare me just this once, I will reform and spend the rest of my life helping those in need—''

``Eh, whose name are you going to swear on this time? You've already sold your parents. Who's a more reliable guarantor than your parents?''

``Just once, ah.''

Chosam Il understands.

The reason the crime of deceit was greater, and why all the masters of Zhongyuan emphasize honesty.

``Where is such a law! What wrong have we actually done!''

Instead, Chosam Il raises his voice in anger.

``Oh, are you going to plead innocence now?''

``This is our Jangyun Sect's territory! What's wrong with a sect protecting its territory and collecting protection fees! You Orthodox sects do the same! You hypocrites! How dare you judge us! What right do you have!''

``No, you didn't protect anything. You didn't do anything, so what protection fees are you talking about?''

``Then are we supposed to starve to death! There's no law in the world that says you should just starve to death! We had no choice but to survive!''

How much food could a small sect like theirs have stored?

With the area under quarantine, they couldn't go anywhere, and they had mouths to feed.

Stealing food from the sick, especially relief grain, was a shameful act, something they couldn't talk about openly.

But should they have just starved?

In desperate times, people even eat their own children, and the state didn't punish such tragedies.

``Should we have just pitied the sick and done nothing! What are we supposed to do! Besides, we didn't take everything! We left them enough to eat!''

Chosam Il shouted in frustration.

But Qing's voice was cold.

``Then you should have helped Langzhong Daren. You should have taken care of the sick together. The elder spared your lives, so I'm only going to destroy your dantian and cut the tendons in your legs. Do you think the elder would have turned a blind eye if you had starved then?''

``That's…''

``You parasites who sucked up the relief grain the elder worked so hard to obtain, while the elder, who had no connection to you, sacrificed his own dignity to feed the sick. And you, the so-called masters of this territory, what about your responsibility? What kind of…''

As Qing spoke, her anger boiled.

-Ah, shit. Thinking about it, I'm really angry. These bastards are just a waste of food. I should just kill them all and face elder's scolding…

It was a chilling muttering.

Chosam Il quietly moved to the right, where the crowd has gathered.

``What's this, why are you all on the left? Are you going to have your dantian destroyed? Are you going to lose the use of one leg? Are you going to end your martial artist life like this? Eh, what's the point of living so miserably? Let's die gloriously.''

``No!''

Qing clicked her tongue and sheathed the Moonlight Sword.

Thinking about it, she could have killed at least one of the leaders, so she should just pretended to be angry and cut them down.

\textit{No, is it not too late?}

\textit{Since they're feeling resentful, maybe one or two?}

``Don't you have any pride as a martial artist! Better to die as a martial artist than live as a cripple! Come at me! I'll yield you three, no, five moves!''

``……''

Instead, the Jangyun Sect disciples lowered their gazes.

Even if she swung her swords and shouted such things.

If the Jangyun Sect were an Orthodox sect, they might have fallen for such provocation, but they're an Unorthodox sect.

And as Unorthodox sect members, they quickly understood Qing's intention.

'She's trying to make an example out of one of us.'

``Not coming out? Fine, I'll be generous. I'll yield ten, no, twenty moves. Still not coming out?''

``……''

-Sigh. Why isn't it working…

Qing muttered softly, and in the tense silence, her voice, even at a low volume, carried a haunting quality.

'Look, she's really trying to make an example out of one of us.'

The Jangyun Sect disciples breathed a sigh of relief, just as that moment passes.

``Tsk, fine, come out one by one. If you try anything funny, it's not your dantian that'll be destroyed, but your stomach. Got it?''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{Destroying the dantian had its own kind of fun.}

\textit{The sensation of a formless mass collapsing isn't comparable to tearing flesh and bursting organs, but the expressions on their faces as their dantian crumbles were uniquely satisfying.}

\textit{The time, the life, even if it's a worthless existence, all the effort they've accumulated evaporates in an instant.}

\textit{And the moment they realize that all their dreams and possibilities for the future have vanished—the emptiness, the dull eyes, the black despair.}

\textit{Yes, killing them would only be a fleeting amusement.}

\textit{But this expression is like an electric current running down the spine, refreshing and thrilling.}

\textit{I'd love to violently shatter their dantian.}

\textit{Let their innate energy leak out, injure their meridians, and let them suffer and weaken until they die, but, hmm, consider yourselves lucky.}

\textit{Even for these scoundrels, if they fall ill, Langzhong Daren will surely try to save them.}

\textit{I can't burden the already busy elder with the trouble of caring for such unnecessary beasts.}

\textit{And besides, how long would they live if left alone?}

Unorthodox sect members were bound to have enemies everywhere.

A cripple who's lost their dantian will soon pay the price for their misdeeds.

Even if not, it's the same.

Can these thugs, who only know how to take by force, changed their ways after being reduced to this state?

Zhongyuan, unlike Qing's homeland, had a culture where the weak get cut down if they act out.

\textit{A culture where acting out gets you cut down, nice.}

\textit{If only my homeland had been like that, it would have been a much more beautiful and humane society.}

Anyway, Qing was a bit regretful, but still somewhat satisfied.

No, she was satisfied.

``Elder, it's all resolved.''

``Are you hurt anywhere?''

``Eh, those amateurs, no, not even amateurs, those martial artist wannabes, how could they hurt me?''

Qing seems oddly relieved.

Langzhong Daren let out a deep sigh and stood up.

``Eh, where are you going?''

``With your temper, would they be unharmed? No matter how cruel they are, I can't just let them die.''

``Eh. You don't have to go. No one's dead, and I neatly cut their tendons, so after half a day of pain, they'll be able to walk, I guess.''

Langzhong Daren paused and asked.

``Fairy, are you actually a Great Master?''

``Of course. I'm a Great Master, aren't I?''

``Do people normally say such things about themselves?''

``What can I do, it's the truth. Wherever I go, I'm about the second or third strongest in the province? I can handle those miscellaneous Unorthodox sects by myself. Ah, these guys are about Mid-level Masters. Not quite Masters, but between Mid and High, Mid-High?''

Langzhong Daren had no interest in martial arts.

\textit{Judging by her boldness and kindness, she must be from a famous family or sect, a bit naive but with considerable skill, traveling freely.}

\textit{But to be second or third strongest in any province, that's saying she was among the top in the world.}

\textit{She doesn't seem the type to lie, and she had no reason to, so if it's true?}

``But why would such a Great Master do carpentry and, what's lacking, squeeze pus from the sick and boil medicine?''

``Carpentry was just something to do during the chaos, and it was kind of fun. Squeezing pus and boiling medicine, you told me to do it, didn't you?''

``Hmm.''

\textit{Would such a Great Master do as told?}

\textit{Help rebuild a city just because they had nothing to do?}

``I thought you're just someone with a powerful background, so I was planning to use that to intimidate, maybe disposing of a few corpses and taking care of a few critically ill patients.''

When Langzhong Daren told them not to kill, it was a request to restrain themselves, not to avoid using lethal force in dangerous situations.

``You should have told me earlier…''

Qing felt wronged.

\textit{You should have been clear about that, the rare chance to enjoy some slaughter!}

``Well, anyway, you did well. We are short on hands, but those guys will at least be able to walk, right?''

``You're going to use them? Hmm, no matter how short on hands we are, they're not the type to take care of patients.''

``Eh, tsk tsk. I wouldn't entrust patients to those who don't know medicine, but there's plenty of heavy work to do. Emptying the latrines, helping patients who can't move, cleaning.''

They've only lost their dantian and become crippled.

The martial arts of small sects mostly rely on external strength, so they've been reborn as cripples who can still use their strength.

So Langzhong Daren plans to make good use of them.

``Then, if any of them don't listen, just let me know. I'll make an example out of a few, and they'll behave, should I do it?''

``See how it goes.''

But Langzhong Daren's plan to reuse these beasts fell apart before Qing can even threaten them properly.

Most of the Jangyun Sect disciples suddenly fell ill with plague symptoms and began to groan in pain.