\chapter{I Don't Like This Kind of Trend (5)}

At Langzhong Daren's words, Qing's face twisted.

``These bastards, they have nothing to steal, so they steal food? Are these even human beings?''

Especially for Qing, it was even more infuriating. 

For Qing, it was a kind of taboo, a memory of a past misfortune where she had to eat something worse than dirt, being the lowest of the low among beggars.

\textit{After a long time, the Moonlight Sword will feast. Among these ruffians who have nothing better to do than steal food from the poor, there's no way a master of the martial arts would suddenly appear.}

With slaughter on the horizon, Qing's eyes gleamed ominously.

``Elder, don't worry. Because, today is, ah, do you know what day it is?''

``What are you suddenly talking about?''

``Today is the anniversary of their death, and every year today was their memorial day. How dare they steal food from the poor and sick? Today, they're all done for.''

Then, thud!

Langzhong Daren's knuckle rap landed on Qing's head.

However, it was nothing more than a small shock to Qing. In fact, it was Langzhong Daren who recoiled from the impact.

With Qing's head being made of indestructible steel, it was only natural that Langzhong Daren's hand would hurt after hitting it.

``Ugh, no, Fairy, what kind of head do you have? It's like a rock. You memorize medical books so easily.''

``Eh? Ah, ouch, ouch.''

It's polite to at least pretend to be hurt when an elder hits you, but Qing rubbed her forehead with a completely unbothered expression.

It was obviously an act, so it only added more wrinkles to Langzhong Daren's already wrinkled face.

``Then it's useless. I made you memorize medical books to save lives, but now you're casually talking about killing people. Even if it's just words, it's not something to say lightly.''

``Ah.''

Qing blinked.

Of course, she weren't particularly surprised.

Qing, being from a future civilized society, had indirectly experienced countless human stories through various media.

She just realized it anew.

\textit{Ah, so Elder Langzhong is this kind of person.}

\textit{Don't even hit with flowers? Non-violence? Life is absolutely dignified and precious?}

Normally, Qing would have preached her favorite philosophy of the inherent goodness of humans. Mencius said that all humans were naturally good beings, meaning that if there's a creature that isn't good, it's not a human but a beast that should be beaten to death—a rather extreme claim.

But Langzhong Daren was truly a benevolent doctor, a saint whose good deeds shone brightly.

It wasn't strange for someone who wandered around saving the needy to say not to kill.

In fact, it was only natural.

``Hmm, Elder. Those from the Unorthodox sects don't listen to just words. In fact, they listen less if you just talk.''

It's the strange pride of the Unorthodox.

It's okay to kneel after being beaten.

But if you yield after being spoken to politely?

Isn't it the way of the Unorthodox to be insulted for yielding without even fighting?

``Huh, so? Are you going to shed blood after all?''

``Ah, not to that extent, but we should beat them up a bit? Just enough to make them limp, so they won't cause trouble later even after we leave. That way, there won't be any repercussions for the people here.''

``Hmm. That's true. Limp, you say? The back of the knee?''

``Yes, the back of the knee.''

It's the vicious communication of those who've studied medicine.

Limp and the back of the knee.

In Qing's hometown, it's called the cruciate ligament.

``Well, if it's just that.''

Langzhong Daren nodded.

Surprisingly, Langzhong Daren agreed immediately.

Like the saying, 'Even if you roll in horse dung, you still want to live',' as long as they don't die, it's fine.

``Alright, you heard? Let's go. What day is it today? It's the day when justice in Wulin iss restored. Heh heh, justice is all done for.''

With that, the corners of Qing's mouth were already tearing, ready to turn vicious.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's ability to act was truly unparalleled.

She act first and think later.

If something came to mind, she didn't hesitate and just go for it, so even if problems arose, it's always after the fact, and she ended up losing out.

This type of person should absolutely avoid gambling or investing.

But.

With a rare chance to feel the thrill of action, Qing's eyes had already rolled back, and they hurriedly strode towards the Jangyun Sect.

``Hmm, but where is the Jangyun Sect?''

``…Aren't you the one who knew?''

``No, it's my first time in this town, how would I know? Zhuge, where are those Jangyun Sect bastards?''

If you don't know, just ask.

However, asking Zhuge Lixian wouldn't guarantee a proper answer.

But since Zhuge was smart, wouldn't they know?

And Zhuge Lixian didn't disappoint.

``Sister, I'm also a first-timer here. How would I know where some nameless local Unorthodox sect is? Hmm, let's go this way.''

Even though he said he didn't know, Zhuge Lixian took the lead.

``Eh? You said you didn't know?''

``But still, the places those who've claimed this town as their territory would think of as auspicious are all around here, right? These small Unorthodox sects are even more brazen, so if we head towards the main road, we'll find it, won't we?''

For a group about to invade another sect, the atmosphere was quite relaxed.

But it couldn't be helped.

Qing was a master of the Flower Realm, and a nameless local Unorthodox sect like this could easily be overturned by them alone.

Pang Daesan, Tang Lan-ah, and Zhuge Lixian were precious direct descendants of the Five Great Clans, so they have nothing to fear from such local sects.

Moreover, with the three Transcendent Realm experts in the group, their strength matches that of a decent local sect, so there's no problem in terms of power.

Of course, Xue Iri and Jian Buxi had no thoughts on the matter.

They just followed Qing as a matter of course.

Zhuge Lixian, who was at the back of the group, quickly found the direction, and before they knew it, the group was passing by the high walls of a large estate.

As they approached the roofed gate, a grand plaque with the characters ``Tae Jangyun'' written in bold strokes came into view.

Qing knocked on the gate.

With each knock, bang bang!

The sound was almost like the gate was about to break.

But there was no response.

``Hello! We've come to deliver good news!''

She shouted loudly, but there was no answer.

Of course, if you say you've come to deliver good news, anyone would pretend not to be home.

But those who come to deliver good news were always annoyingly persistent.

Qing placed both palms on the gate.

Bending her waist like a bull, she pushed, and with a creak—

Qing's strength was no ordinary strength, and the wooden hinge pin couldn't hold and popped out, causing the gate to slowly fall backward.

Crash! The gate fell with a loud noise.

Qing stepped over the fallen gate and shouted at the top of their lungs.

``Hey! The service is was absolutely terrible! Owner, come out!''

Behind her, the group exchanged glances.

'She's really excited, huh.'

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

``Sect Leader, it's them!''

``Hmm. Isn't this too fast?''

Chosam Il, the sect leader of the Jangyun Sect, scratched his chin.

However, he wasn't particularly flustered.

After all, he had expected them to come.

He had received reports that Langzhong Daren had brought some young martial artists.

Young martial artists who followed Langzhong Daren into the quarantine zone where the plague was rampant.

They must be from the Orthodox sects, so-called chivalrous knights who were still immature.

Moreover, Langzhong Daren must see them as a thorn in his side.

Young martial artists were reckless, ignorant of the ways of the martial world, and act solely on impulse.

So it was only a matter of time before they came at the old man's behest.

But still, isn't this too fast?

They must have rushed here as soon as the old man spoke.

``Tsk. Those from the Orthodox sects. They see the Unorthodox as inherently evil.''

``Sect Leader?''

``Alright. I'll go see their faces.''

Chosam Il stood up.

As he walked to the front courtyard, the disciples lined up in a row.

Pushing through the disciples, he saw the figures of the young martial artists.

A woman with a veil, a man, and a muscular giant.

And three stunning beauties.

And, what's this, a kid?

At that moment.

The woman with the veil, whose presence was overwhelming despite her face being covered, spoke in a mocking tone.

``Are you the owner here?''

Chosam Il was taken aback.

It was an impolite remark, not even used among the Unorthodox.

It wasn't something to say to the leader of a sect.

Unless they were picking a fight.

But Chosam Il held back.

Judging by their attire, they were from noble families, and to travel the dangerous martial world with such beauties, they must be no ordinary youths.

Moreover, bringing a child along meant they had the confidence and skill to invade even with a child in tow.

To provoke so openly, they must be even more cautious.

``Ahem, I am Chosam Il, the sect leader of the Jangyun Sect. Where are you noble guests from?''

``I am the Earthwork Fairy! I was once a carpenter, then a fairy, hmm? Fairy? No, not a fairy, a doctor. Thus, the world calls me the Earthwork Fairy! You ugly creatures! How dare you exploit and plunder the poor who are struggling with illness, are you even human beings?''

The Earthwork Fairy?

What kind of title was that? It's unheard of, and such a title didn't exist.

In other words, it was a blatant insult.

It was a provocation that anyone could see was meant to incite a fight, which oddly calmed Chosam Il's anger.

``Ahem. There seems to be some misunderstanding.''

``Misunderstanding my foot. What misunderstanding?''

``Our sect is currently in seclusion.''

``…Eh.''

The veiled woman's momentum visibly weakened.

Chosam Il continued with a pitiful voice.

``Exploitation and plunder? That's also a misunderstanding. Isn't it the way of the martial world? We take care of the local security and receive a modest tribute. But Langzhong Daren said, 'How can you demand tribute from the poor suffering from illness?' I felt deeply ashamed. So we decided to close our sect's gates.''

``…Really?''

``To be honest, it's more about shame than anything else. There's no reason to antagonize someone of Langzhong Daren's stature. Even if we're from the Unorthodox and get insulted, going against the wishes of such a renowned figure would bring consequences we can't handle. So we've closed our gates.''

Seclusion was like a temporary closure for a shop.

By locking the gates and doing nothing, the sect members can no longer act in the name of the sect.

Behind the veil, Qing's brow furrowed.

\textit{Indeed, the elder had said the same.}

\textit{They said they wouldn't do it, but then they started secretly taking again, didn't they?}

\textit{But whether they really took protection money from the sick after that, Langzhong Daren only had suspicions, not concrete evidence.}

\textit{No matter how much they questioned the patients, they all insisted they hadn't been robbed.}

\textit{But if the patients really hadn't been robbed?}

\textit{Langzhong Daren said that they were eating less because their food was being taken, but if you're stuck in a quarantine zone with nothing to do all day, even a healthy person would feel sluggish, right?}

\textit{Now what?}

Qing straightened their slouching posture.

``Is that statement certain?''

``I swear on my parents' names, it is true.''

\textit{Wait, swearing on their parents' names here?}

\textit{Isn't that a professional term for perjury?}

\textit{This won't do.}

Given the evil deeds of the Jangyun Sect, their words aren't trustworthy.

And Langzhong Daren didn't seem to be mistaken, so it's likely they're just using the seclusion as an excuse to avoid the immediate crisis.

But it's not certain.

She was planning to cripple them so they couldn't do such things again.

But just because they're from the unorthodox and have a high record of evil deeds, and because the process of subduing them was fun and enjoyable, isn't it a bit much to act on that alone?

What if there's even a one in a million chance they're truly innocent?

So, what? They should retreat for now and gather evidence, not just suspicions but concrete proof.

``Ahem, we'll retreat for now.''

At that, a smug smile appeared on Chosam Il's face.

``Ah. The Earthwork Fairy, was it? Once a carpenter? Then fix the gate before you leave.''
