\chapter{I Don't Like This Kind of Trend (6)}

The Earthwork Fairy, who had suddenly barged in, ended up retreating just as weakly.

However, the general manager of the Jangyun Sect looked uneasy.

``Big Brother, iss this really okay? What if they come back later, accusing us of lying and causing trouble…''

It was a confession that would have immediately drawn Qing's furious nuclear strike if they had been present.

But Qing wasn't there, and the sect leader of the Jangyun Sect, Chosam Il, was full of confidence.

``Kid, you've got no guts, no guts at all. Let them dig around all they want. Those kinds of people are just passing through. Who do the locals see all the time? Us, right? If they're sane, they wouldn't dare make a fuss.''

This was the reason why whistleblowing within groups, big or small, was nearly impossible.

Unfortunately, life doesn't end just because a chivalrous tale was concluded.

When a chivalrous hero appeared, stirred things up, and meted out justice, it's satisfying for the moment, but then what?

Sadly, those left behind had to continue living, bearing the full brunt of the aftermath.

Moreover, the term 'young chivalrous heroes' wasn't exactly used in a positive sense.

``Do you think those brats in fancy clothes can last a few days here? Taking care of the sick? I guarantee they won't last three days before running away.''

Helping those groaning from illness?

There's an old saying, 'In the face of long illness, even filial piety fades'. Taking care of the sick was a dirty, miserable task, one that even parents struggle with.

How could these impulsive brats, who barged into another sect without a second thought, possibly endure it?

Chosam Il had his logic and reasoning.

But, as another saying goes, 'What you see is what you are', he assumed everyone's character was at his level.

``As expected of Big Brother.''

``But the Earthwork Fairy? The way she fixed the gate didn't look like it's her first time. Is that really her title? Has anyone heard of it?''

The half-hearted taunt about fixing the gate was partly out of annoyance.

After all, what's wrong with collecting protection money in this line of work? These clueless brats, who don't understand how the world works, dare to talk back to their elders. Of course, it's infuriating.

But the annoyance was only half of it.

There's no better way to drive away kids than by humiliating them.

Kids, when humiliated, tend to slink away quietly.

The plan was to embarrass them by making them struggle to fix the gate, then laugh at them and drive them far away.

But what?

She smoothed the corners, used a knife to whittle, and quickly hammered the hinges and nails.

In no time, the gate was fixed.

Even the creaking sound was gone, and it opened and closed smoothly, showing the skill of a trained carpenter.

But that was only for a moment.

Chosam Il dismissed it casually.

``Well, aren't there all kinds of weirdos in the martial world? Anyway, for now, let's keep a low profile and stay quiet. You know what I mean, right?''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Langzhong Daren heard the report, he was dumbfounded.

``What? So you just came back meekly, fixing the gate like a lamb?''

``What else could we do? Should we have forced the issue and crippled them?''

``You should have. There's no scum worse than those who prey on the sick. As you said, you should have broken their legs.''

It was an unexpectedly harsh statement.

Qing realized something anew.

\textit{Hmm, Langzhong Daren really believes that as long as I don't kill, it's fine.}

But Qing didn't retreat for no reason.

``What if what they said was true?''

``You believe that? Fairy, you're really naive.''

Langzhong Daren clutched his chest.

But Qing had her reasons.

``Even if it's just one in a million chance. If they're the kind of people who would go into seclusion just because you said something, then for Unorthodox sect members, they're somewhat decent. Isn't that better than other scum taking over after the plague subsides?''

Unorthodox sects were like rats or bugs.

Even if you sweep them away, others will appear.

If they're the kind to go into seclusion just because of public opinion, then as Qing said, they're among the better ones in terms of character.

If Qing swept them away and some truly vicious ones take their place, who would suffer the consequences?

Langzhong Daren nodded at that.

``Right, Fairy, I've always known you're deep. You must have had a plan. That makes sense.''

Qing's companions were doubly dumbfounded.

Once by Langzhong Daren's quick change of stance.

And twice by the comment about Qing being deep.

``So, Elder, we should have made sure before leaving. Is it certain that they're preying on the sick?''

``Ha, would I make that up?''

``Not just suspicions. There must be a reason you think so.''

``Look at what the sick excrete. If people eat, it should come out one way or another, right? But it's not coming out in the amount they're eating. We carefully measure and distribute the food daily, so there's no reason to hoard it. Who else would be stealing it?''

``Could it be someone other than the Jangyun Sect?''

``Who else would be roaming the town stealing food? Maybe one or two quack doctors, but if the latrines aren't full, who else would be doing such things?''

``So they're not eating as much as they're given. It's not certain it's the Jangyun Sect, but, hmm, circumstantially?''

\textit{Ah, what was it?}

\textit{After eliminating the impossible, whatever remains must be the truth, right? Who said that famous quote?}\footnote{Sherlock Holmes}

Qing's mind wandered briefly, recalling a famous quote but couldn't remember who said it.

But Qing also knew that no matter how much she pondered, there was no way to recall the proverbs or song lyrics from her homeland.

Memories of home were fading.

For a moment, it was nostalgic, but that was all. Qing easily shook off the sentiment.

``Then, we'll have to ask the victims directly. These bastards, just wait until we catch them.''

``Hmm, Sister. It won't be easy.''

``Eh. Why?''

``We can leave whenever we want, but the sick have to stay, right? They'll be too afraid of repercussions to speak up. No matter how angry or wronged they feel, it won't be easy.''

``Eh. Why?''

``If it's the Jangyun Sect's doing, they're quite clever. They're not stealing all the food, after all. They leave enough for the sick to survive, so the victims would rather maintain the status quo than risk making things worse.''

``Eh. Why?''

There were two ways to make people angry: one was to leave a sentence unfinished—

If you want to make someone angry, just stop here.

Thus, few know the second, more effective way to anger someone.

This precious second method was simply repeating the same thing.

Zhugei Lixian's eyebrow twitched.

But it was only for a moment.

``Why make it complicated? Just ask if they've been robbed or not. If you don't try, you'll never know, right?''

Zhugei Lixian's mouth hung open in shock.

It was a slap to the back of the head!

There were plenty of reasons why asking wouldn't yield an answer.

Unless they're villagers in the countryside, city folk, especially in bustling cities, don't fall for the illusion of chivalry.

They're too familiar with the antics of self-proclaimed chivalrous martial artists.

Even the fights that break out in inns were proof enough. To the common folk, whether they're gangsters or chivalrous heroes, they're all the same—troublemakers who leave without cleaning up their mess.

So even if the group questions the Jangyun Sect's crimes, the sick won't readily open up.

Moreover, how much did common folk really know about Wulin?

Anyone with a sword was scary.

Among them, old martial artists were scarier than young ones, unorthodox sect members were scarier than orthodox ones, ugly martial artists were scarier than handsome ones, and groups were far scarier than individuals.

Thus, to the common folk, the Jangyun Sect members were much scarier and more intimidating than Qing's group.

But does that mean they shouldn't even try?

Zhugei Lixian deeply reflected.

``I've made a grave mistake.''

``Right. As long as you realized it, that's enough. And, hmm, maybe we can just ask?''

``Do you have any insights? You're occasionally quite sharp, Sister.''

``I do. First, let's have San show his face.''

At that, Peng Daesan's expression soured.

``Why me?''

``Why not? It's a beauty trap. You show your face, give a deep look, lower your voice—''

Qing mimicked Peng Daesan's voice.

It didn't sound like him at all, despite the effort to lower the voice.

``'Young Lady, your beauty is filled with sorrow, and my heart aches for you. Who dares cast a shadow over you? May I have the honor of helping you?' Kyaaah! That'll end it in one go, won't it? Even if there's no grudge, we'll create one and stir things up?''

Peng Daesan's expression turned sour.

It was a natural reaction for Peng Daesan, who detested such things.

``Why should I be the one to do the beauty trap? You, hmm, no. That one over there, no. Hmm.''

Peng Daesan was somewhat convinced.

A beauty trap isn't just about being beautiful. The idea of 'those over there' flattering and catering to a man's ego was unimaginable, utterly impossible.

Though Qing's sworn sister, Jian Buxi, was an option.

But it wasn't something to bring up lightly, given the sensitivity.

``What! Are you done spouting nonsense?''

That one, Tang Lan-ah, snapped angrily.

That two, Xue Iri, sharply raised her eyebrows.

``Ah, San. If it would work, I'd have done it myself.''

Qing spoke apologetically.

Knowing Peng Daesan's aversion to women, it was indeed a reckless suggestion, but wasn't this all for the sake of accumulating good deeds?

``Men naturally become stronger in front of women they're interested in. If someone's bullying them, they'll deny it even if it kills them. So if I ask if the Jangyun Sect stole their food, they'll never admit it, right?''

``Hmm…''

Pang Daesan let out a low growl.

He had nothing to say, but his reluctance was clear.

``I know you don't like it, but can't you do it just this once? Huh? Don't you know about chivalry? Sometimes, you have to endure for the sake of justice. Kyaaah, this is what chivalry is. San is so cool! San is so kind!''

To put it bluntly, Qing was just mimicking a kindergarten teacher coaxing children from their homeland.

But Pang Daesan unknowingly let the corner of his mouth twitch upward.

\textit{Only when it's convenient does she sweet-talk and act cute, huh? Like when she's hungry.}

\textit{In Luoyang, she drew the line at her own affairs, starting fights and leaving on her own, but now she's asking for help outright.}

\textit{Maybe there's no other way-}

``And it's not like we're doing this for personal gain. Whether it's the Jangyun Sect or some other scum, we should take down those who prey on the already suffering. Right? No, thinking about it, it's infuriating. Are these even human beings? Stealing food from the sick because there's nothing else to take? They'd even steal tears from a chick. When I catch those bastards, I'll slaughter them—''

The anger escalated naturally.

It was a gradual buildup of rage.

Pang Daesan let out a deep sigh.
