\chapter{I Don't Like This Kind of Trend (4)}

The place where the patients were gathered was Banryong Street in the northern part of Kunming. Surrounded by mountains on three sides like a protruding horn, it was the perfect terrain for isolation.

They thought they would head straight to Banryong Street, but Elder Langzhong led them to the Kunming market instead.

``Welcome, ah… Elder, you've come.''

A grain merchant, who had been spreading out sacks of various grains to sell, hurried out to greet the customers but didn't seem particularly pleased to see Elder Langzhong.

At first, they thought his customer service was just poor, but then…

``Elder, you still haven't paid off the credit from last time. Of course, feeding the sick is a good deed, but I also need to make a living, don't I?''

``Tsk. Such stinginess. A grain seller worrying about starving to death when there's grain everywhere. How much could the credit even be?''

``It's already up to ten silver coins. And that's without any profit margin. I gave you the grain at cost because you said it is for a good cause…''

``Did I take the good grain? It was all old stock. Where's the profit in that? Tsk. What are you doing? You want money, don't you?''

Elder Langzhong looked at Qing's group as if it were obvious.

Even though he had taken the entire money pouch, he was still pressing for more.

Perhaps he was trying to save some money for the patients after they left, but his attitude was so bold that Qing glanced at her friends with an embarrassed expression.

This time, Zhuge Lixian stepped forward and opened his money pouch to settle the debt.

While it's hard to believe there was a merchant who claim to sell without profit, the relieved expression on the grain merchant's face suggested he wasn't lying.

``Alright, how much old grain do you have left?''

``Ahem, how much do you need?''

``All of it.''

``If you take rice, barley, beans, and millet, it'll be about seven bushels. Are you saying you want all of it?''

``Are you deaf? I said all of it. This big guy from the Zhuge Clan will pay, so don't worry about the credit.''

``Ah, you're the young master of the Zhuge Clan.''

Zhuge Lixian scratched his head.

Although it seemed like Elder Langzhong was specifically targeting Zhuge Lixian to pay, he was also subtly framing this grain donation as an act of charity from the Zhuge Clan.

If this was how he 'extorted' money from the rich to help the sick, the wealthy probably didn't feel too bad about it.

After stopping by the grain merchant to buy rice, wheat, barley, and other cheap, old grains instead of fresh ones…

``Are you sure old grains were okay? We could buy some better ones while we're at it.''

``Tsk, do you know what a lockdown is? They just round up the sick and lock them away. Where do you think the money comes from? After just a month, you'll become the poorest of beggars. What kind of doctor would bother with such a den of beggars, unless they're as strange as me?''

Elder Langzhong shook his head.

``So what can I do? I don't have much money either, so I have to save where I can. The taste might be a bit off, but if it fills your stomach, it's good enough. When people are starving, they'll eat anything as long as it fills them up.''

As they made their way through the market, Elder Langzhong bought up all the old grains from the grain merchant and loaded them onto carts. He also bought the cheapest cuts of meat.

He only bought the cheapest items, except for medicinal herbs.

``Look here. When you're buying herbs, you have to dig through the bottom. Those scoundrels always hide the watered-down stuff at the bottom. See this? For Bai Ling grass, you only need to check the ends. Even if it looks withered, as long as the ends are alive, it's fine. And even if it looks fresh, if the ends are dry, it means they've sprayed it with water to fake its freshness. You should be careful when buying herbs too.''

``Ah, Elder, you make it sound like we're playing tricks. We just added a bit of water to keep it fresh…''

``Listen to this guy. All herb sellers are like this.''

Elder Langzhong clicked his tongue repeatedly.

He rummaged through the herb sacks while continuously explaining how to distinguish good herbs from bad. It was like a hands-on lesson.

However…

``Uh, Elder, is it really okay to dig through the sacks like this?''

``Of course not.''

Elder Langzhong grinned mischievously.

``Normally, if you dig through the sacks like this, you'd get kicked out. But if you're famous, you can get away with it. Fairy, you're a master, right? If anyone complains, just pull out your sword and ask if they want to die.''

``Ohh…''

The herb merchant was speechless.

'What kind of 'ohh' is that? This eccentric old man is acting like he's teaching something profound.'

``And you, girl from the Tang Clan, listen carefully. Knowing herbs ss the foundation of medicine.''

``Hey, I know how to identify herbs too!''

``Hmph. The Tang Clan of the world probably doesn't even deal with cheap stuff. But you need to know how to identify even these withered herbs. Can you do that?''

``Hmph. Why would I bother with such shabby things?''

``Because not all patients in the world are rich. Everyone knows that good herbs are better, but if you're treating more than a few people, you have to save where you can. Here, this is stone mint. The leaves need to be bigger than two segments for the medicinal effect to work…''

``Ugh, this is so shabby…''

Tang Lan-Ah grumbled but listened intently.

After finishing their rounds at the market, they had seven carts trailing behind them.

All filled with cheap items, but even these were bought on credit at every stop.

It made Elder Langzhong's virtuous deeds all the more apparent.

Even if he 'extorted' money from the rich, the wealthy weren't the type to give it up easily.

The rich were either extremely greedy or have inherited their wealth from greedy ancestors.

If an old man came around using his reputation to strong-arm them, they might donate some out of face-saving, but it wouldn't be enough.

Hence, every stop had unpaid credits.

\textit{Despite his rough and stubborn demeanor, it must have been quite humiliating for an old man to go around begging for favors.}

\textit{Hmm. As expected, Elder's Good Karma is not without reason.}

As they headed toward Banryong Street with the carts, a wooden barricade blocking the city came into view.

She thought the lockdown would be guarded by soldiers, but they had gone as far as physically blocking the area with felled trees.

The soldiers stationed at the temporary gate in the barricade looked troubled.

``Elder, only medical personnel are allowed through. The others—''

``They're all doctors. Doctors.''

``But Elder, they clearly look like martial artists.''

``Can't martial artists be doctors?''

``But there's even a child here.''

``She's a medical apprentice. Medicine is something you have to learn from a young age.''

``Ahem, this really isn't acceptable.''

But what could a lowly soldier do?

In the end, they had no choice but to open the gate under pressure.

Once inside, a group of people rushed over to greet Elder Langzhong.

``Elder, you're here!''

``Everyone, come get your food. There's meat today, so while it's not a lot, at least you'll have some broth and something to chew on.''

``Ooh, we'll finally get to taste meat! Thank you, Elder!''

``It's not me who bought it. Where would I get the money? These young folks paid for it, so thank them.''

``Thank you!'' ``Ooh, thank you!''

The flood of gratitude softened Qing's group's expressions.

Even the lingering suspicion that Elder Langzhong might be a fraud began to melt away.

After all, isn't this the feeling that makes people volunteer and do good deeds?

Then, everyone rushed to unload the carts.

They parked the carts halfway through the gate, and the quarantined people of Banryong Street began unloading and stacking the supplies.

Once the cart drivers left, the gate was firmly closed again.

The sound of the bar being slid into place followed.

Then, some people naturally grabbed bowls and began opening the grain sacks.

Everyone lined up to receive their share of grain, vegetables, and meat, a scene so familiar it was almost comforting.

Qing expected some squabbling over who got more, but everything was orderly.

It was a rare sight in Zhongyuan.

At that moment…

``Look over there. Take a peek. Those guys.''

``Huh? Who?''

``Those guys over there. They look downright nasty.''

Qing followed Elder Langzhong's gaze.

Sure enough, a few individuals stood out.

She couldn't tell if they looked nasty, but they were noticeable.

Probably because, amidst the generally ragged and dirty crowd, they were relatively clean and well-dressed.

Moreover, they weren't in line but stood off to the side, observing the distribution.

``Those bastards deserve to drown in a cesspool.''

``Who are those guys?''

``They're from the Jangyun Sect, a bunch of thugs. They can't shake their old habits and are extorting ‘protection money.' What kind of protection are they offering in a situation like this? They'd even pluck the eyes out of a chick.''

The Jangyun Sect was a common rogue faction.

Banryong Street, protruding to the north, was surrounded on three sides by the steep slopes of Gongwang Mountain.

These steep slopes were shortcuts for those who knew how to climb mountains, making it a popular spot for mountain climbers.

Originally, Banryong Street had a decent-sized market where mountain climbers sold their harvests.

And in Zhongyuan, wherever there's a market, there were martial artists collecting protection money. The Jangyun Sect had claimed this area as their territory.

However, when the area was locked down, the Jangyun Sect was also quarantined.

``Does that make sense? It's not like they were suddenly blocked off. They must have been warned to leave beforehand, right?''

``Hmph. That's how martial artists are. If your sect was told the area would be locked down and to leave, would you just obediently go?''

``Hmm.''

``Besides, don't martial artists all think they're some kind of big shots? They probably thought they could ignore the lockdown.''

They might have believed they were above the law due to their martial status.

Or perhaps, since local sects usually bribed city officials, they thought they'd be exempt from the lockdown as usual.

``It's ridiculous. Unless they're as powerful as the Diancang Sect, how could a small Unorthodox sect like them defy a national quarantine order? Even the military is involved in this.''

``Sister, they probably had no choice. For Unorthodox sects, losing their territory was like being annihilated. Without their income and base, their members would start deserting immediately. They probably thought it was better to stay inside the quarantine zone and hold on.''

Zhuge Lixian interjected.

No one had asked, but he offered his opinion anyway.

``So what? Are you saying they're extorting protection money from the sick now?''

``Exactly. That's why I went to confront them.''

Qing was shocked.

An Unorthodox sect with no future or prospects—why would an old man who doesn't know martial arts go to confront them?

What if something happened to him?

But Elder Langzhong just snorted.

``Those kinds of people are all bark and no bite. If they harmed Elder Langzhong, every sect in the area would come after them. What could those puny thugs do?''

``Still, it's dangerous.''

``Anyway, I went and confronted their sect leader, and he apologized and promised not to do it again.''

``Huh? He promised not to do it again?''

``That's what I thought. But those bastards only pay lip service. We ration the food daily, but no one gets enough. When I asked people if they were extorting protection money again, they denied it. Of course, they'd deny it. Who'd admit it with armed thugs around?''

They're probably still secretly extorting.

In a completely locked-down area, armed thugs were the most intimidating figures.

So even though Langzhong worked hard to bring food, people were still going hungry, their faces turning yellow.

When asked if the Jangyun Sect took their food, everyone was too scared to admit it, so there's no evidence.

Elder Langzhong had been racking his brains over this when, by chance, a group of wealthy young people entered the city and started spending money lavishly.

Troublesome as it was, he couldn't let people starve.

So he went to seek some charity and ended up like this.