\chapter{I Don't Like This Kind of Trend (3)}

The old man's exposed skin was deeply wrinkled, making him look about a hundred and fifty years old, if we were to use the professional term 'face value'.'

Despite his age, he stood straight and sturdy, without a hint of a stoop, which alone gave him the aura of an immortal.

However, the term 'immortal's demeanor' isn't always used in a positive sense. Among the most famous immortals of Zhongyuan, there were quite a few eccentric figures, such as Zhongli Quan and Li Tieguai.

By the way, Zhongli Quan and Li Tieguai were members of the Eight Immortals, the most prominent figures in Taoism, known for their unattractive and shabby appearances.

Langzhong Daren was no different, with his deeply wrinkled cheeks and a face that seemed to sag with age.

To anyone looking at him, he didn't appear to be a doctor but rather a grumpy, ill-tempered old man, full of spite.

``Greetings? What kind of greeting is needed for a wandering old man like me? And am I even in a position to receive such formalities? Enough of that.''

Langzhong Daren waved off the group's attempts to bow and then extended his hand toward Qing.

``Well. Give me some money.''

He spoke as if he had entrusted his money to her.

The old man boldly stretched out his hand, but Qing was no less bold in her response.

As if it were the most natural thing in the world, she untied her entire money pouch and placed it in the old man's hand.

Langzhong Daren quickly snatched the pouch, peered inside, and then let out a sly smile.

``Kekeke, this is quite heavy. Kehehe, I'll put this to good use. This should last me for a while. Maybe I can even try a few new things.''

At this, Qing's friends exchanged glances.

After all, the old man's appearance didn't exactly inspire confidence.

An old man drooling over gold, claiming he'll use it for good—what could go wrong?

But Qing already knew.

Surprisingly, he really was the type to use it for good.

Just now, he had mentioned that he would spend it freely to try new medicines and treatments.

After happily inspecting the gold coins in the pouch for a while, Langzhong Daren suddenly turned his head.

``Hmm? Why are you all just standing there staring? Well, good. You all look like the precious children of wealthy families. Why don't you make a charitable donation while you're at it?''

Langzhong Daren wasn't just interested in Qing's money; he also had his eyes on the group's purses.

Qing, however, gently held onto Langzhong Daren.

``Ah, Elder, let's not rush. Please, sit down for a moment. You look quite worn out. Have you been eating properly?''

``Hmph. Do you think I'd be doing this if I had enough to eat? If I had money, I'd be brewing more medicine.''

``Ah, but if you collapse, what good will that do for your patients? Since we've met by chance, let's replenish your energy. They say food is the best medicine, after all.''

``Ha, where did you hear such nonsense? I've never heard such absurdity in my life.''

Langzhong Daren snorted.

But after a moment, he frowned slightly.

``Well, I suppose it's not entirely baseless. Those who collapse from hunger often spring back to life with a good meal. So, I guess food can be medicine.''

Langzhong Daren quickly took a seat.

In Zhongyuan culture, it's customary to refuse an offer at least once, even if you intend to accept it.

Sitting down immediately after being invited to eat, without any hesitation, was considered quite rude, though not to the point of being scolded.

``This is Jian Buxi, my sworn sister, and this is Ciyu, my daughter. And…''

Qing introduced the group.

But Langzhong Daren was too busy piling food onto his plate to pay much attention.

Then, without waiting for anyone, he began to devour the food, as if it were going to disappear.

This was incredibly rude, but to Qing's group, it wasn't surprising, as they had seen Qing eat like this many times before.

However, while Qing ate with a greedy yet joyful expression, Langzhong Daren's eating was purely voracious, as if he were swallowing without tasting.

This was a stark contrast to the rumors of Langzhong Daren, who was said to wander the land, providing medical care to the poor without charge.

'Isn't he just a shameless old beggar?'

The group began to seriously wonder if he was an imposter or a fraud.

``Ugh, ah, that was good.''

``You're already done?''

``Of course. Food is just to fill the stomach. You've eaten enough too. Let's wrap things up and get going.''

``Huh?''

``What do you mean, ‘huh'? Don't you want to go? Aren't you going to see the patients?''

Qing blinked rapidly.

``Uh… Elder, I'm actually on my way to the Diancang Sect right now.''

``Oh? Did someone at the Diancang Sect collapsed?''

``No.''

``Then will someone die if you don't go?''

``No, it's not like that—''

``What do you mean, ‘it's not like that'? No one at the Diancang Sect is going to die if you don't go right now. But if you help me, you could save at least one or two more lives. What could be more important than saving lives?''

``Uh, hmm. Should I go right now?''

Qing wasn't the type to be easily swayed by others, but this time, the situation was different.

After all, the glowing blue numbers above the old man's head indicated a level of virtue she had never seen before in her travels.

Moreover, the deep-rooted respect for elders ingrained in her hometown's culture made it impossible for her to refuse.

Langzhong Daren was, without a doubt, her natural nemesis.

``Then are you going to wait until they die? Or are you going to wait until all the patients are dead before you go?''

``Hehe, that's not what I meant. Let us at least arrange for some proper lodging first. After helping you, Elder, I can—''

``What do you mean, ‘lodging'? A single swordsman can do the work of ten strong men. Why leave the others idle? Let's all go together.''

``Wait a minute! What kind of nonsense is this?!''

Tang Lan-Ah's sharp voice echoed through the room, cutting off the conversation.

Tang Lan-Ah was a notorious troublemaker from Sichuan, someone who didn't care about age or status.

She was the type to speak her mind, even to elders, and she had no qualms about saying what others wouldn't dare.

"And what is so special about this so-called famous doctor? Our Tang Clan has doctors too, and we help the poor just as much. What's so great about Langzhong Daren?"

Tang Lan-Ah was the kind of woman who always spoke her mind, no matter the situation.

The only problem was that she often said more than she should.

``Didn't you say there's a plague? And you want to take her into that? If she gets infected, will you take responsibility?''

``Ah, well, then maybe I should just help—''

``Qing, this isn't as simple as you think. I know you're too kind for your own good, but do you know why it's called a plague? It's because no one knows what it is. The most terrifying disease is the one even doctors can't identify. Who in their right mind would go into an area with an unknown disease?''

Langzhong Daren status suddenly turned into 'crazy old man'.

But Tang Lan-Ah's words were undeniably true.

The most dangerous disease was the one whose nature was unknown.

Without knowing whether it's contagious or not, one can't even determine if it's safe to approach the patients or touch their wounds.

Moreover, without understanding the symptoms, one might not even realize they've been infected until it's too late.

From Tang Lan-Ah's perspective, even if Langzhong Daren was praised throughout the land, and even if his intentions were to save lives, this wasn't a matter to be taken lightly.

But could Langzhong Daren really be unaware of these dangers?

``Ah, you little… If anyone hears this, they'll think I'm trying to lure a naive child into danger. I'm not asking for help with a contagious disease. If it were dangerous, I wouldn't even ask for help.''

``Hmph! You say it's not contagious? Then what kind of disease is it? Shouldn't there be a name for it?''

``Ahem, well…''

Langzhong Daren trailed off.

After all, if the disease had a name, there would be no reason for rumors of a plague to spread.

People would know exactly what disease was going around.

At this, Tang Lan-Ah placed her hands on her hips.

``See? I knew it. How can you be so sure it's not contagious if you don't even know the name of the disease? If it turns out to be contagious, you'll just say, ‘Oh, it was contagious after all,' right?''

``Ah, you little brat, how dare you talk back to your elders? I'm the doctor here, not you. If I say it's not contagious, then it's not. Do you even know anything about medicine?''

``Hmph! I'm a doctor too, you know? The Tang Clan of Sichuan is known for its medical expertise. How dare you talk about medicine in front of me?''

``Ha! These days, everyone thinks they're a doctor. What kind of doctor can a little girl like you be?''

``What did you say?! If you're going to spout nonsense about women not being doctors—''

``What are you talking about? I've studied medical texts for decades to earn the title of ‘Langzhong,' and you, a mere child, dare to call yourself a doctor?''

At this, Tang Lan-Ah was momentarily speechless.

The term ``Langzhong'' originally referred to shamans who practiced medicine.

In the past, medicine was not considered a science or skill but rather a form of magic or sorcery.

It wasn't until the Tang Dynasty that the court gathered the langzhongs, compiled medical texts, and established medical schools to teach medicine. From then on, those who healed people were called doctors or scholars.

Since then, the term ``Langzhong'' has had two meanings.

One was an old-fashioned, respectful term for a doctor, and the other was a derogatory term for a quack who might be practicing medicine or sorcery—no one knows for sure.

Usually, it's used in the latter sense.

This was because charlatans who sell so-called miracle cures often use grandiose titles like ``Langzhong of the World'' or ``Divine Langzhong'' on their banners.

So Langzhong Daren's words weren't just a rejection of Tang Lan-Ah's medical skills but a reflection of a taboo in Zhongyuan medical circles.

'I've spent decades studying medicine to earn the title of Langzhong, and you, a mere child, dare to call yourself a doctor?'

But Tang Lan-Ah couldn't respond without undermining her own professional pride as a female doctor.

``Anyway, it's not contagious. Do you think only the patients are in that area? There are family members taking care of them, as well as those who couldn't leave due to illness or stubbornness. It's been two months since the lockdown, and no one else has been infected. It's not contagious.''

If two months had passed without any new infections, then it was more than enough time to conclude that the disease wasn't contagious, even if its nature was still unknown.

\textit{Hmm, if Langzhong Daren is saying this much, it seems the disease isn't highly contagious.}

\textit{After all, in the locked-down northern part of the city, there wre not only patients but also their family members who have stayed to care for them, and they're all fine.}

\textit{Moreover, the cosmic mystical energy grants immunity to diseases, so if ordinary people are fine, what about martial artists who have cultivate Qi?}

\textit{So maybe I can stay for a while and help—}

But then Qing suddenly tilted her head.

``Elder? Didn't you say there are many family members of the patients still inside? Then why is there a shortage of help? Not that I'm trying to avoid going.''

At this, Langzhong Daren hesitated.

``Ahem. Did I not mention it? Of course, swordsmen are useful in many ways, but what I need right now is a swordsman.''

``You need a martial artist?''

Langzhong Daren snorted.

``There are always a few scoundrels in the world, but among them are those who try to take advantage of the sick. Those bastards deserve to drown in a cesspool.''
