\chapter{I Don't Like This Kind of Trend (2)}

It felt as though time had stopped.

The guard, frozen in the act of inspecting a pouch, reminded me of a street performer from my hometown, creating an eerie and mystical atmosphere.

In the flow of time, only he remained still.

Soon, the guard's expression darkened.

He carefully examined the silk pouch I had roughly handled, turning it over and over, as if searching for some damaged spot. Then, naturally, he knelt down, clasped his hands together, and raised them high in a respectful gesture.

``My apologies for the inconvenience. You there, hurry up and load the luggage! Quickly! But be careful! No, hurry! But gently!''

``Huh? Is the inspection over?''

``Yes, it's a matter of national importance. If you had informed us earlier, we wouldn't have troubled you so much. We were merely performing our duties, so please don't be upset.''

His face was pale, and his trembling voice, shaking from fear, made me feel almost sorry for him.

Ah, right. I had that inspector's badge.

I had tucked it away in my pouch, thinking I wouldn't need it.

The city gate guard was still trembling.

Some hero's uncle once said that with great power comes great responsibility, but in reality, great power often comes with great wealth and authority.

The inseparable trinity of power, wealth, and authority grants the ability to evade responsibility for any wrongdoing.

In other words, the greater the power, the lesser the responsibility.

This exempted responsibility includes trivial and mundane acts like following the rules and standing in line, which were expected of ordinary citizens.

Such lowly acts were unbecoming of those in power.

By the way, this mindset has led people in the Zhongyuan to view cutting in line as a natural right, a way to value oneself.

Anyway, if a mere gate guard were to incur the wrath of someone powerful, a simple pointing of the finger and a command to ``cut him down'' would instantly end his livelihood.

Stopping a high-ranking official trying to pass quickly under the guise of national law was like a fairy tale—no, it's a lesson straight out of a fairy tale.

Or so I thought.

``No, it's a critical time. There's a plague going around, right? So we have to be thorough, even if it takes time.''

I waved my hand dismissively.

It's understandable that the guard was irritable and unfriendly. When people have endless tasks piled up before their eyes, it's natural to feel that way.

And closing the city gates at night isn't just a local decision here in Kunming; it's a national law observed in every city.

``But what's the situation with the plague?''

I seized the moment to ask casually.

I had no intention of posing as an inspector, but I didn't want to miss this opportunity either.

``Yes! Right now, we're isolating patients in the northern part of the city and enforcing a lockdown! We're also searching for doctors in nearby villages to prepare for any incoming patients, and we're strictly monitoring all entries and exits!''

The plague had appeared two months ago.

Of course, Kunming only became aware of it two months ago, so it must have spread much earlier than that.

Already, patients within the city were vomiting blood from the plague.

So the Kunming magistrate and his deputies had gathered the patients and locked them down, strictly inspecting all entries and exits to prevent the spread of the disease.

``Hmm. What about Dali? Is it chaotic there because of the plague too?''

The Diancang Sect was located on Diancang Mountain.

And behind the long, narrow Diancang Mountain lies a large city, which was Dali County.

It was also my destination, heading towards Diancang.

``Don't even mention it.''

The guard shuddered.

``Those Bai people, those bastards, they must have spread the plague. They're all fine, while Han people like you, sir, and other ethnic groups were dying left and right. They say it's an old endemic disease of theirs, so they're immune, but everyone else was dying. They say you can catch it just by getting close to those Bai people.''

Yunnan Province was originally the land of the Dali Kingdom, a realm of barbarians.

And the Bai people were the descendants of that Dali Kingdom, the ethnic group to which the royal family of Dali belonged.

So the Bai people of Dali held a status similar to that of the Han people in the Zhongyuan.

And now, among those dying from the plague, not a single Bai person was affected.

Nearby villages were also in chaos due to the plague, but the Bai villages remain unaffected.

Even within Kunming, the plague first broke out in the northern district where the Bai people live, yet the Bai people themselves were all fine.

Hmm.

Is it like how the Europeans brought some terrible disease to the New World, and the plague was immune to the Bai people but deadly to other ethnic groups?

It seems to make sense.

And Dali County was the capital of the former Dali Kingdom, a city of the Bai people in Yunnan Province.

If the Bai people were spreading the plague, as the guard says, then Dali County, being a Bai city, would be the most dangerous place, wouldn't it?

Well, there's nothing to be done about it.

I've come this far, so it would be awkward to tell them to go ahead. I'll just have the kids wait in Kunming and return together later.

From here to the Diancang Sect was about nine hundred li.

It's quite a distance, but if I rush there, take a quick look at the Absolute Sword Cliff, and come back, it should be quick…

But still, was it really okay?

The sorcery enthusiast, Danryun Jinin, said that my constitution was resistant to poison and disease, but it doesn't have a self-purification function.

What if I become a carrier or something? If I turn into a plague bearer, I can't just casually return, can I?

As I pondered, the guard's rant about the Bai people continued, though it was mostly just complaints.

They've always been like that, those barbarians, acting all high and mighty while eating strange things, not even realizing they're sick.

They boil pangolins and bats, and I knew it from the start.

Eating pangolins and bats caused the plague? This was just like…

Hmm. But pangolin was delicious…

And actually, pangolins and bats were eaten in many places in the Zhongyuan.

The Zhongyuan people eat anything that moves—if there were bats, they eat bats; if there were pangolins, they eat pangolins. They even eat animals that aren't dangerous and were easy to catch.

The saying that Zhongyuan people eat anything with four legs except tables didn't come from nowhere.

``Especially those Dali bastards—''

``Captain, we've finished loading the luggage.''

The endless tirade against the Bai people came to an end with a subordinate's report that the luggage had been loaded.

``Ah, well, good work for now.''

``Yes, sir! We'll continue our duties!''

The guard, now full of military discipline, saluted loudly and saw me off.

And so, I entered the city of Kunming.

Compared to the previous city, Qujing, which was overflowing with travelers, the streets of Kunming were relatively quiet.

Of course, the strict inspections at the city gates meant that fewer travelers were passing through, so it was only natural.

Thus, when the carriage arrived in front of Kunming's premier inn, Manchunlou, a group of waiters rushed out and almost plundered the luggage.

Fearing that I might go to another inn, they first unloaded the luggage, much like the behavior of beasts in my hometown that hook onto vehicles first and ask questions later.

Normally, a premier inn representing a city wouldn't engage in such rude behavior.

A city's premier inn wouldn't need to resort to such rudeness to attract customers.

But Kunming was one of the largest cities in the Zhongyuan, and even its premier inn was behaving this way.

This alone shows how much business has been affected by the plague.

After unloading the luggage…

It was an awkward time for dinner, so I ordered a bath to wash away the fatigue accumulated from traveling.

I tend to get spoiled when I have attendants, so after a thorough bath and feeling refreshed, I started to feel hungry.

Then, I ordered a lavish meal, and the waiter, smiling broadly, seemed delighted amidst the business downturn.

``Oh? Is this Sichuan cuisine? How's the spiciness?''

``The numbness was a bit lacking, but it's decent.''

The numbness refers to the Sichuan people's peculiar preference for a tingling, numbing sensation that almost paralyzes the mouth.

The pride Zhongyuan people have in their hometown cuisine was so strong that arguments can escalate to the point of drawing swords.

Among them, Sichuan was one of the regions known for its fiery cuisine, and if Tang Nan'a, a Sichuan native, says it's decent, then it must be authentic Sichuan cuisine.

Kunming cuisine was essentially a less numbing version of Sichuan cuisine.

This was also characteristic of Yunnan Province, which resembles the surrounding regions in many ways.

Of course, Yunnan also has its own local dishes.

``Ahhh, this was so good, ahhh.''

Finally freed from the sour and tangy broth, I was enjoying a proper hot soup to my heart's content.

It was Yunnan-style rice noodles, with chicken broth simmered until an oily layer formed, served separately from the noodles and toppings.

The steamed duck dish, using mallards instead of domestic ducks, was also highly praised.

While I was eating, I heard some commotion outside.

My hearing, which surpasses that of ordinary humans, picked up the sounds of an argument.

``Oh no, you can't do this.''

``What do you mean I can't? Move aside, now!''

The one pleading was the inn's waiter.

The other was a gruff but seasoned old man.

``Oh, sir, we've just received a precious guest after three days. Please understand our situation. We're really on the verge of ruin here.''

``Ha, the premier inn of Kunming was going to ruin? That's a story even a dog wouldn't believe. Move aside, or do I have to throw you out? Move!''

``Oh no, sir, please! If you cause trouble again—''

``Trouble? Did you just say I'm causing trouble? You need to watch your mouth! In a fancy inn like this, where people eat expensive food, can't I ask for a little help? Is that trouble? Is it? Let's share some gold coins and eat cheap food together! What, were the rich going to catch the plague from eating cheap food?''

Hmm, so he's barging into a high-class inn to extort money from guests.

Isn't that usually called trouble?

And he's not asking for copper or silver coins but gold coins, saying the rich should share.

Hmm. Is this old man planning to wave a red flag and rally people with some revolutionary spirit?

``Move! You!''

``Oh no, sir, please, please!''

``You won't let me pass? If anyone hears, they'll think I'm causing trouble to extort money. I'm just asking for gold coins to use for a good cause! For a good cause!''

This was also a common excuse used by extortionists.

Using it for a good cause means using it for their own good cause.

``Hey, look at this guy! He's grabbing an old man! Everyone, look! The waiter was grabbing an old man!''

``Oh no, this won't do! Just step on me and go! Sir! Sir!!''

Hmm. If he says to step on him, of course, I'll step on him.

An old man boldly demanding gold coins, not even silver, wouldn't hesitate to step on a waiter.

Qing looked towards the inn's entrance with a mix of anticipation and curiosity.

\textit{This feels like the prelude to an inn brawl.}

\textit{Is it time for the villain's appearance?}

Pushing aside the curtain, the old man boldly entered to extort money.

\textit{Wait a minute.}

\textit{His face looks familiar, though the person I know isn't that old.}

\textit{But now that I see his face, his gruff voice matches, so why didn't I think of it earlier?}

Qing stood up and bowed respectfully with clasped hands.

``Greetings, Elder. How have you been?''

The old man paused.

He stared at Qing face for a moment, then his eyes lit up with recognition.

``Aren't you Fairy? What are you doing here?''

``Ah, so that's how it was back then. Hehe.''

Actually, in an inn with no other guests, you don't need superhuman hearing to eavesdrop on the argument at the door.

Her companions, who could be considered experts by ordinary standards, were also present.

So, everyone was preparing to deal with the unruly guest when they suddenly became confused.

'What's this? Do they know each other?'

Qing introduced the old man to her companions.

``Guys, give your greetings. This elder is Langzhong Daren.''
