\chapter{Xi-Mung Qing (3)}

The Demonic Cult's patrol envoy comes to deliver an ultimatum!

Of course, no matter how much they were enemies, there was no harming of envoys.

Moreover, the recipient was the Wulin Alliance, the headquarters of the Orthodox Wulin.

Rather, they had to protect the patrol envoy carrying the ultimatum from being attacked.

It was necessary to avoid giving the Orthodox Wulin a pretext for vilely harming an envoy.

Thus, the Wulin Alliance Masters dispatched for this purpose surrounded and watched over the envoy from an awkward distance, unable to get too close as they couldn't associate with those dirty Demonic Cult bastards, providing both surveillance and escort.

In this way, the Demonic Cult's infamous black ebony carriage, surrounded by a layer of Masters, crossed Zhongyuan, with eyewitness accounts spreading all the way to the Wulin Alliance.

And in front of the Wulin Alliance headquarters…

There was already a sea of people who had come to watch.

Even a Wulin tournament wouldn't have drawn such a crowd.

However, although no one said it out loud, everyone had a general sense of what the Demonic Cult's patrol envoy's ultimatum would be.

A final ultimatum!

An ultimatum refers to a diplomatic letter sent from one power to another.

Among these, the very last, final ultimatum is precisely that - a final ultimatum, meaning 'There's no need for dialogue anymore, let's have a go at each other'.

This implied an important fact for the Wulin Alliance.

How confident must those Demonic Cult bastards be to declare war and come charging in!

If those who usually gathered their forces and struck with surprise attacks were now giving advance notice…

However, the power of the Orthodox Wulin was also at its peak.

Since the Celestial Martial Emperor, the level of martial arts in the Orthodox Wulin had been reaching new heights every day, so even if the wicked Demonic Cult came charging in now, they would rise up valiantly to face them.

In front of the Wulin Alliance's main gate, the Alliance's key figures lined up in a row, holding their weapons.

This was the Wulin Alliance headquarters, imbued with the spirit of the Orthodox Faction.

It was a display meant to show that they couldn't allow the filthy Demonic Cult's spawn into the Wulin Alliance.

One might say this was all unnecessary.

However, in Zhongyuan, a matter of face was as important as life itself.

The Demonic Cult's black ebony carriages appeared through the crowd of onlookers.

An ominous murmur spread in waves.

"Halt!"

A lion's roar imbued with Buddhist merit resounded loudly.

The pure energy, one which almost seemed to exterminate demons, that the Inner Light Master of Shaolin had honed through a lifetime of martial studies spread widely.

It was a kind of psychological warfare.

It had an effect; the ominous murmuring noise suddenly stopped.

Admiration for Shaolin, saying they were indeed worthy of being called the head of the Orthodox Wulin, briefly followed before subsiding.

Then, what the emboldened people did next was jeering and criticism.

"How dare the Demonic Cult's evil spawn invade here!"

"Boo! Get out, you Demonic Cult bastards!"

"Did you think the Orthodox Wulin would be intimidated by this? Justice always prevails!"

Amidst this, the patrol envoy finally raised the ultimatum high and shouted.

"While wishing for your Alliance's eternal glory, on behalf of the Divine Cult's Supreme, I announce to the virtuous experts of the Wulin Alliance!"

"…?"

"…?"

For a moment, silence hung in the air.

Everyone blinked with expressions that seemed to ask, 'What did I just hear?', looking around at each other for confirmation, but all wore equally dumbfounded expressions.

At least this confirmed that they hadn't misheard.

"The new Divine Cult's Supreme wishes to erase old grudges and hatred, and see an end to the long-standing animosity! To this end, we open the doors of the Divine Cult and seek reconciliation, hoping to break free from the chain of sorrow where hatred begets hatred and pain begets pain, and instead sing joyful songs together under the heavens!"

\textit{Oh shit, we've been had.}

The Wulin Alliance warriors broke out in a cold sweat.

If they had welcomed the patrol envoy inside the Alliance, it might have been different, but if they sought reconciliation in broad daylight in front of people from all over Zhongyuan, the Alliance had no choice but to accept.

The Wulin Alliance needed the Demonic Cult to attack first to have justification. As protectors of peace and tranquility in Zhongyuan, they couldn't refuse and declare that reconciliation was unnecessary and that they wanted war.

From the beginning, hiding their true intentions and disguising it as if they were going to deliver a final ultimatum was all a ploy for this purpose.

The warriors uselessly racked their supposedly good brains.

It was a characteristic of clever people.

But what was the true intention behind this?

If what they truly wanted was peace, this could become a historic moment where one of Wulin's long-standing troubles disappeared.

But what if it was just a ploy to induce complacency and spark the Fifth Great War between Orthodox and Demonic?

"Now that the doors of the Divine Cult are wide open, any virtuous expert of Wulin who wishes may visit the Divine City of Tian Shan and see for themselves!"

"Hmm."

The warriors let out an uncomfortable groan.

A door, by nature, allows passage in both directions.

By merely opening the thatched door of their remote foreign village, weren't they saying they would also advance into Zhongyuan?

However, there was no particular justification to stop them.

The long-standing grudge was indeed from long ago, so even if they said they had suffered from the Demonic Cult, it was mostly just learned from hearsay.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The journey from Sichuan to the Divine Maiden Sect wasn't really much of a trip.

Just get on a boat and get off. That's it.

Of course, the scenery along the Yangtze River was beautiful.

From the Min River in Chengdu, one would take a boat and follow the waterway to join the main stream of the Yangtze River.

Without disembarking, they would then straight to enter Chongqing in the eastern part of Sichuan Province.

Chongqing was also one of the sweetest lands where kings emerged.

The term 'Ba-Shu' commonly used to refer to the Sichuan region combines the lands of Ba and Shu, with Ba referring to Chongqing.

As a result, while Sichuan people are considered eastern Sichuan, Chongqing people get upset when lumped together with Sichuan folks, asking not to be associated with them.

After passing through the long, narrow land of Chongqing horizontally, one would immediately come across the Wu Gorge, considered the most scenic part of the Yangtze River.

And the highest peak of the Wu Gorge is the Divine Maiden Peak.

When the sailors call out "We've arrived at Wu Gorge, come out and take a look!", Qing could just quietly prepare and disembark at Zigui, and she would be right at home.

In modern terms, the Divine Maiden Sect has a Yangtze River view and its own Divine Maiden Sect station, making it a super-prime real estate!

With the return journey being so convenient and close, it was no wonder Ximen Surin rushed out upon hearing news of turmoil in Sichuan.

When a disciple who could return in just a few days if she wanted to (though the Yangtze is only fast one way) was dawdling and not showing her face, of course she would be full of worry and chase after her.

Thus, upon arriving at the mountain gate of the Divine Maiden Sect, Qing finally let out a big sigh of relief, feeling overwhelmed with emotion and thinking 'At last, I'm home'.

While it's true that in terms of luxury, the Divine Maiden Sect couldn't compare to either the Demonic Cult or the Tang Clan, the mental stability that comes from being in one's own home is something that can't be provided anywhere else in the world.

"The Grand Sect Leader has arrived. Gulp."

The Divine Maiden Sect disciples tended to be severely intimidated by Ximen Surin.

So, as soon as they entered the sect, she flew off on her sword saying she had to water the orchids, which was Ximen Surin's consideration to let them enjoy their reunion time with the Divine Maiden Sect disciples they hadn't seen in a long time.

"Great Junior Grandmaster! Wow, you've become even more beautiful! You are literally Xi Shi! You are literally Yu Miaoyi! You are literally Diaochan! You are literally Wang Zhaojun!"

Xi Shi refers to the most beautiful woman of all time, Yu Miaoyi's\footnote{wife of Xiang Yu. The 'Miaoyi' given name is invented in 2012's TV series} full name is not known, Diaochan is Diaochan, and Wang Zhaojun is sometimes called Wang Zhang because her name was Zhang. It was roughly the Four Great Beauties minus Yang Guifei.

"What? The Great Junior Grandmaster is here?"

"Great Junior Grandmaster!!"

"Great Junior Grandmaster, where did you go this time? Can we come listen to your stories?"

"Can't you play the flute for us? It always lingers in my ears, but it doesn't feel the same unless it's you, Great Junior Grandmaster."

"Who's the person next to you? A new disciple?"

"Wow, the Most Beautiful Woman in Sichuan! The Speaking Poison Flower!"

"The Flower Rain! Can you show us the Flower Rain?"

"You idiot, wouldn't we all die if she did that?"

They were in an uproar, chattering among themselves.

Qing received their enthusiastic welcome, putting a piece of candy she had brought into each of their mouths.

The children who lived in the mountains without going outside the sect were not only very kind but also extremely sensitive to external stimuli.

So it was almost like an attack by a flock of birds.

Unlike Qing, who was already used to it and skillfully popped a piece of candy into each mouth, Tang Lan-ah already looked visibly tired.

"I imagined something quiet when they said it was a Daoist sect, but…"

"Isn't that all just prejudice?"

"Qingcheng and Emei were quiet, you know. But you, you really were a Daoist elder…"

Tang Lan-ah spoke as if seeing Qing anew.

Of course, her attitude was already different from when she was staying at the Tang Clan, so it couldn't be helped.

She had been completely relaxed, with laziness ingrained in her body. There was a moment when she seemed to be training a bit with Peng Chaolei during the journey, but even that didn't last long.

All she did was sleep, eat, or cling to Old Choi and act spoiled.

But now that she was home, her waist was already straightened, shoulders broadened, looking like a dignified Elder Sister, so it couldn't help but be surprising.

Qing chuckled and said.

"What do you mean, elder? First, let's go greet the Sect Leader and then I'll guide you to the guest quarters."

As they were crossing Divine Maiden Peak like this, something small suddenly ran up and threw itself into an embrace.

"Ack! I hurt my chest, you know? Don't rub your face on the wound, please?"

"Gasp."

It was an unfamiliar face.

But it was a little one wearing a Second-Grade Disciple training uniform, whose crown just reached a bit below the collarbone when hugging.

While Qing was tall for a woman, standing just two finger-widths short of six chi (5'9.4"), even considering that, not reaching the collarbone was still quite small.

There was only one person in the Divine Maiden Sect who fit that description.

"Oooh. Changming'er. You've become very pretty. I almost didn't recognize you."

"Heuheut."

Chen Changming made a strange laughing sound.

Qing looked her up and down and exclaimed in admiration.

"Oooh. What's this? Are you around the Early Stage First-Rate Realm now?"

"Hehehehe."

At this, Chen Changming put her hands on her hips and acted smug.

Qing continued speaking.

"A mere First-Rate nobody shouldn't be blocking a Peak Realm Master's chest. Won't you move aside? Go play with other Early Stage First-Rate novices. Oh no, I might catch the First-Rate disease. Shoo, shoo. Go away."

"Tch."

Chen Changming's face soured.

As Qing chuckled and opened her arms again, Chen Changming hesitated and asked.

"Which side is hurt? Left? Right?"

"Left."

"Okay."

Chen Changming threw herself into an embrace again.

Qing let out another short scream.

"Ack! That's the left side. It just barely healed, and now it's going to split again."

"What? You said left, didn't you?"

"It's my left, you know? Not when you're looking at me."

"Then you should have said so."

"When someone asks if your left or right arm is hurt, do you answer based on their left? You're saying such stupid things even after so long has passed since we've met."

"Hmph."

"Alright. Now let go. The law is strict, and minors shouldn't be clinging like this."

"…? I've been an adult since we first met."

"To me, men and women are the same. It starts from the age of twenty. Changming'er, you're eighteen this year? Two years left."

"One year and one month. This year is almost over."

For reference, in Chinese coming of age, men were considered adults at twenty, the age of capping, while women were just fifteen. Literally only fifteen years old.

When a man was fifteen, they were told to set their mind on learning and told them to 'Embrace Learning', but for women at fifteen, forget learning, they were just told to hurry up and have children and were considered adults.

This was how things were in Zhongyuan, which was why Ximen Surin was so indignant and wrote down countless legendary anecdotes of women's struggles.

Then she looked at Tang Lan-ah and asked.

"Who's this?"

Thunk.

Qing lightly flicked her forehead.

"What kind of manners are those towards a guest? This thing is Tang Lan-ah. She's one of the Five Great Beauties of Wulin, and also, um, a physician."

"Hey! How can you call a person ‘this thing'. Uh, hello? Junior Daoist?"

"Five Great Beauties?"

Chen Changming looked at Tang Lan-ah's face, then at Qing's face, then checked Tang Lan-ah's face again, and then looked at Qing's face with a snort and raised one corner of her mouth crookedly.

"Hey! What's that, you little thing! What's that supposed to mean?"

"Hmph."

Qing suddenly recalled an old memory at this sight.

\textit{Come to think of it, this Changming brat has been a little shit with no manners since the beginning.}

\textit{I forgot because she acted so docile after entering the Divine Maiden Sect.}

\textit{Well, maybe she just had severe anxiety when it came to strangers or something.}
