\chapter{Xi-Mung Qing (7)}

A woman dressed in silk climbed the mountain path of Mount Wu.

It wasn't really an outfit that suited this season.

When it comes to high-end winter clothing, it is made of a type of silk called kun (綑) or chou (綢), and is woven so that it remains fluffy and does not twist even when filled with cotton.

However, the best of silks is called jin (錦), which is thin, fluttering, and soft, so that even if the cotton is just a little lumpy, it will rise up and form flat wrinkles, so even if it is well-beaten, it is only suitable for wearing in the spring and autumn.

The woman was wearing this garment made of gold.

On the other hand, she put a lot of effort into her makeup, with her hair twisted and covered in gold accessories, her skin coated with white powder, her eyes painted with lavender pigment, and her lips smeared with a reddish color.

However, the woman's appearance was so naturally alluring that the added makeup made her look overflow with a sultry, sexy aura.

So, when the woman appeared in front of the Divine Maiden Sect gate, the disciples of the second generation who were standing guard at the main gate swallowed dry saliva.

At first glance, it doesn't look like the kind of attire you'd wear to a temple.

Even if it's a guest visiting during lunch time, there should be an apology or an urgent look, as it would be rude, but there is none of that.

The two disciples exchanged glances.

'Senior, a seductress has appeared. What should I do?'

'How would I know? You'll have to find out for yourself.'

So, the junior looked into it.

This was because there was a hierarchy within the guard duty.

"Halt. From here on out is the sacred territory of the Divine Maiden Sect. Are you wishing to make ancestral rite?"

“Aha. I came to the right place. Yes. That’s right.”

Suddenly, the disciples of the Divine Maiden Sect drop their vigilance.

They are disciples of the Divine Maiden Sect who spend their time with women, day and night, so they can infer her personalities  from that one speec.

She only looked seductive, but her voice and tone were full of a sense of silliness.

She's just a pretty face, but she's so innocent.

The Divine Maiden Sect is the forbidden for men.

On the contrary, its door was  wide open for women.

Even if they are not disciples, they occasionally receive female worshippers and earn extra income.

"Welcome. Are you planning to pay your respects? Or are you planning to stay in the temple for a while? Or are you planning to make offerings?"

“No, that’s not it. My Sworn Sister said she was here…”

“Ah. You came to see your little sister.”

The woman looked to be in her mid-twenties, so her sister must be a Third-Rank disciple.

Because the disciples of Second-Rank are all familiar with each other's family history, they knew she's not among their generation.

The attitude of the disciple of the The Divine Maiden Sect became even more relaxed.

“What is your younger sibling’s name?”

“It’s Ximen Qing…”

"Yes?"

"Yes?"

"Oh. Isn't this the place? She clearly said the Divine Maiden Sect. She's this tall, and her breasts are this big."

The woman gestured broadly, drawing a circle in front of her chest.

The disciples the the Divine Maiden Sect understood immediately.

'Ah, it's Junior Grand Master.'

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Qing ate lunch, she acted as if lunch was her parents enemies.

It meant that they couldn't live under the same sky, so se chewed it up and swallowed it whole to get rid of it.

By the way, the same goes for breakfast and dinner.

It was while Qing was inhaling the boiled and stir-fried vegetables.

“Sworn Sister!”

“Oing?”

Qing's eyes widened at the familiar voice.

"Sworn Sister, you shouldn't be wearing such thin clothing. You'll catch a cold. It's already cold outside, so you have to be careful."

“Ah. That’s right.”

Qing, who had been separated for a long time, finally reunited with her long lost Crutch.

\textit{Why would you wear outrageous clothes in this weather?}

\textit{You look prettier now? Is it because you put a lot of effort into your makeup?}

Of course, it's thanks to makeup.

Of course, Ximen Xi did gain minor achievement by taking the elixir given by the Divine Cult, but wasn't makeup originally a woman's greatest weapon?

“Have you eaten?”

“No. I got lost a bit on the way up. Hmm. I’m hungry. Hehe.”

“Then we should eat. Our food is delicious.”

"Yes!"

And then she went out to get her food.

"Who?"

“What the heck is that? Why are you wearing makeup like that and coming to eat?”

Chen Changming and Tang Lan-ah asked at the same time.

“Uh… something like a Sworn Sister?”

\textit{What does that even mean? Either she's Sworn Sister or she's not, pick one.}

The two of them looked at each other with a confused expression.

Actually, Qing is not sure either, so she didn't explain it further.

And then Ximen Xi, who has a big appetite, came back with a mountain of food on a tray.

“Oh. Right. I decided to be Jian Buxi again?”

“Huh? Why?”

"They say it's weird when sworn sister have the same family name. And since I'm the older sister, people will find it even stranger. And even if your parents didn't do anything for you, you shouldn't give up your family name carelessly."

“Did Xue said that?”

"Eung."

“Well, that would be right, then.”

\textit{If Xue Ganom, the most intelligent person in the neighborhood, said so, then it would be natural.}

\textit{Among the people I met in Zhongyuan, he was the most trustworthy person, aside from my master.}

\textit{Come to think of it, Liu Bei, Guan Yu, and Zhang Fei all had different surnames, so they weren't unified as Liu Bei, Liu Yu, and Liu Bei.}

\textit{Even then, there would be two Liu Bei's.}

“Oh. What do you think? Don’t I look pretty?”

“Did you put on your own makeup?”

"Yeah. I learned it. Should I teach it to Sworn Sister later? No, should I teach it now?"

“It's fine. It’s a hassle to erase it.”

“Right. That’s right.”

“But why the makeup?”

“Xue, no, that’s what Mister told me to do. He said that if you look easy wherever you go, nothing good will come of it.”

“Ah. You call that Xue Ganom ‘Mister’?”

"Yeah. But it's a bit like that. I think I should call him Sister Xue. Sometimes I just blurt it out without realizing it."

“What, that guy got prettier”

“No kidding. It’s like, he really like a sister.”

"Should I look him up? I'm really curious..."

Chen Changming and Tang Lan-ah, who got sidelined, thought.

\textit{What? Doesn't this usually when you introduced the guest?}

\textit{Is your field of vision narrow and you can't see the person next to you?}

"Ah. So this is the flavor Sworn Sister likes. Would you like some more? Should I give you some?"

“No. I already ate a lot.”

“Sister, who is sheu?”

It seemed like she'd would have to listen for the rest of her life, so Chen Changming interrupted.

"This is Jian Buxi, and, um, she took care of me for a while. She's like a Sworn Sister. She's the one who helped me out in the Jianghu."

“Hmm. Hmm.”

Jian Buxi nodded as if she was proud.

"The kid here is the baby of our sect, Chen Changming. This woman is Tang Lan-Ah, the Poison Flower. She's a friend. You've heard of the Five Flowers of Zhongyuan, right"

"Yeah. But when I saw it on my way here, I felt like I'd been completely fooled. Well, Mr. Xue told me not to say anything, so I can't say anything anymore."

"I know what you mean, so it's fine. I asked that Xue guy to teach you some common sense, and looked like he did a good job."

“Ugh. But it’s so annoying.”

"It'll all becomes flesh and blood. Do you think it's easy to find a teacher like Xue Ganom?"

"Ung……"

The eyes of the women on either side of the blue narrowed.

\textit{What? Isn't it usually the time for self-introductions?}

\textit{Yeah, is that all you'd say?}

The two thought as one person.

\textit{This girl is no pushover.}

If Qing had known, she would have just laughed.

Where else you can find the most easygoing person in the world?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Jian Buxi's admission into the Divine Maiden Sect was not successful.

It was because of her origins, and the martial arts she had learned were the Bangjungsul, which used both Unorthodox Yang and Unorthodox Yin.

"What would a child like that do at the Divine Maiden Sect? It's not like she'd have to disperse all her Inner Qi and learn from scratch. If she wanted to, I could at least write a letter of recommendation for the Heavenly Flower Hall. But I don't think that child wants it."

Besides, Jian Buxi had no particular intention of becoming a monk.

After finishing the meal, she tried to carry Qing, but after hearing that Qing had to do everything herself at the Shinnyeomun, se realized that there was no need to become a priest.

Instead she would help Xue Ganom with his work in the city below and then follow her when she goes on a journey to the Jianghu.

"Still, for someone from the Demonic Cult, she's quite pure. A bit lacking, but she's a very good child."

“Is it just a bit lacking?”

Whack! A light flick touched Cheong's head.

It didn't hurt because it didn't meant to be hurting.

“No matter how true it may be, it is not right to speak carelessly about other people’s faults.”

"Yes."

"It would be nice to take her with Disciple when you go out into Jianghu. Even if that old man cherishes Disciple, shouldn't a woman be the one to take care of a woman's needs?"

“Sure, she’s comfortable.”

“Just think of it as raising a person. Wouldn’t all of that kind of thought accumulate into good karma?”

Cheong tilted his head.

\textit{Isn't it a bit harsh to treat Sworn Sister like that?}

Of course, Jian Buxi deserves it.

"That's a good arrangement. When Disciple go to Kaifeng next month, I can't send that old Demonic Adept along."

“Huh? Me? Why?”

"I heard the Wulin Alliance is holding a martial arts competition. There must be more than a few people who recognize that old man. How can a great Taoist elder goes there without losing face?"

The purpose of the martial arts competition was to strengthen unity before the opening of the gates and the advancement of the Demonic Cult into Zhongyuan.

At this time, if you appear with a top figure of Demonic Cult, then you are no better than an idiot even if you are clueless.

By the way, Ximen Surin, who was talking about an old man, was older than Choi Riong.

Although she appears to be a beautiful woman in her forties, she is actually a living legend and a senior martial artist.

"But what about the martial arts competition? Is it some kind of world-class martial arts competition?"

"I'm sure there will be some big names here and there. As for this master's greed, I wish you'd attend the Dragon Phoenix Assembly."

“Then let’s go, okay?”

It was a direct answer without a single moment of hesitation.

Ximen Surin smiled brightly at her.

\textit{She was a disciple who I couldn't help but admire.}

“Since there will be no one who can match Disciple anyway, it would be better to think of it as raising the reputation of our sect and just be beautiful and elegant.”

The term "십초지적" means an opponent that can be defeated with just ten moves, and in technical terms it is also called "ㅈ밥".

The number of sparring sessions has already reached a level where its length should be counted rather than the number of times.

If Ximen Surin were to categorize her disciple's level, it would be at the Late Peak Realm, but she had already gained an advantage over Transcendent Realm in life-and-death battle.

Moreover, since she has already reached a level where she felt the sensation of the sword as an extension of her body, she is on the verge of achieving Sword Unification in the near future.

If it is the union of the new swords, then isn't it an enlightenment that can only be obtained in the Late-Stage Transcendent Realm, after one has freely wielded the sword?

So, even though the order is a bit messy, she's still achieving steady results.

\textit{At this point, I had to start wondering if there was another reason why she couldn't reach the enlightment.}

\textit{It's as if something is blocking it tightly.}

\textit{In terms of Inner Qi, she is already on par with the Unrestrained Realm Masters, and in terms of external skills, it makes you wonder if she is even human, but why can't she just get over that superficial and easy wall of Transcendent Realm?} (this is the opinion of the Profound Realm master).

“So, I just have to go and win?”

"Come hang out with the kids from the Nine Sects. You should get to know the future leaders of the Orthodox faction, right?"

In other words, she was telling me to go hang out at a social gathering.

Even though technically Qing is an elder of the Divine Maiden Sect, her status isn't exactly the same with the more established sects.

Moreover, personal connections are especially important to the Chinese people.

Even though the Divine Maiden Sect may be inferior to the Five Great Nobles, if they show overwhelming martial arts skills at the Divine Dragon Competition, it will naturally be resolved.

“If that’s the case, then I’m an expert.”

Qing's eyes sparkled.

\textit{If you tell me to come play, of course I'll be happy to.}