\chapter{Xi-Mung Qing (5)}

Tang Lan-ah suspected the Divine Maiden Sect's disciples physically and emotionally abused Qing upon seeing her state.

Especially for the delicately raised Tang Lan-ah, it was a shocking sight that caused cultural shock.

A single piece of thin, see-through cloth was draped over her with two shoulder straps.

Moreover, one shoulder strap had frayed and broken, so it was roughly tied, making it unbalanced left and right.

However, she soon realized it was a misunderstanding.

"Ah, Junior Grandmaster, you're wearing that again? Wow, you're still so beautiful. I'm really jealous."

"Why, do you want to try it on too?"

"Later when it's hot. It's too cold now. Can't you let me wear it when it's warm and we're alone?"

"Wake up and stop dreaming. How could I give this to you when it's so comfortable in hot weather? If you're not going to change into it now, forget it."

And then there was a passing auntie, no, a First-Grade disciple.

"Junior Master, I sewed two blankets together and put in plenty of cotton, so use that. Oh my, just looking at you makes me cold."

"Wow. Thank you so much. You're truly my lifesaver."

"If you're grateful, don't just say it. Next time when you go out into Jianghu, you know?"

"Noted. I'll properly repay your kindness, so look forward to it."

And then, the Third-Grade chicks.

"Great Junior Grandmaster! Flute! Flute! Flute!"

"What the… Did I leave my flute with you or something? Did I owe you a flute performance? Do I look like a flute to you?"

"Hurry, hurry. We've been waiting for Great Junior Grandmaster to come. Don't you have any new songs?"

"Let's see…"

Qing quickly plagiarized some eternal classics and played a few tunes, causing everyone to go wild with delight again.

Everyone accepted Qing's attire as extremely natural, creating scenes where they would either make a fuss about how pretty she was or show not even a speck of disregard.

Well, everyone was already familiar with this sight after seeing it to the point of nausea last year, and stimuli tend to raise the threshold when continued.

They might have been excited last winter, but by this spring, they were more interested in the flute recital than her clothing.

At this point, even Tang Lan-ah was confused.

\textit{What's going on, am I the weird one?}

\textit{Isn't it indecent to wear such a see-through, unsightly thing as clothing?}

\textit{Isn't Qing'er ashamed as well?}

However, Qing just rubbed her arms saying it was chilly, but walked around without any particular sign of embarrassment.

\textit{I don't know what's happening.}

\textit{If neither she nor others make an issue of it, what's the point of me being concerned?}

\textit{But why do I feel so thirsty every time I look at her?}

And so Tang Lan-ah just kept swallowing hard and eagerly watched.

However, she couldn't just follow Qing around all the time, as the Divine Maiden Sect disciples thoroughly made use of the physician who had rolled into their sect.

It was to the point where it was confusing whether she was a guest or an invited physician, as the naturally industrious people of the Divine Maiden Sect couldn't stand to see anyone being idle.

Especially when even the youngest Junior Grandmaster of the Sect Leader's generation, who came later, was dedicating herself to training all day with just a thin cloth wrapped around her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After spending about half a day copying, Qing got a rough idea.

Unexpectedly, there seemed to be quite a lot of free time.

The books of Zhongyuan had fewer characters than Qing had thought.

Moreover, her physical strength, concentration, and basic dexterity were unlike those of common people who didn't know martial arts, resulting in an enormous work output.

At this rate, she could finish leisurely over the winter and go back out into Jianghu in spring.

Qing felt relieved thinking this.

After wrestling with ink all morning like that, she was in the middle of thoroughly demolishing the Divine Maiden Sect's lunch, which wasn't fancy but was neat, deep in flavor, and above all, provided infinitely.

A First-Grade disciple asked with a worried expression.

"Junior Master, are you sick?"

"Huh? No. I'm fine."

"The Grand Sect Leader was worried that you might be sick since you didn't come to morning training. Are you just playing hooky?"

"Huh?"

Only then did Qing realize her mistake.

It wasn't training material, it was homework!

And then one question came to mind.

Even if she did the copying leisurely, it was still an amount that would take all winter until spring.

\textit{If I go to Master in the morning and afternoon…}

\textit{Wouldn't there be no time left?}

\textit{No wait, then when would I sleep…?}

However, for Ximen Surin, the books she had given Qing were merely basic knowledge for learning.

Allocating separate time to acquire such very basic background knowledge?

She was a cold-blooded person who couldn't understand such a concept itself.

"What rush is there? It is not like Zhongyuan are begging my disciple to come. You can finish slowly, so should you not learn properly before going out? Will you die if you cannot go out in spring? Tsk. Look at how you are so full of thoughts of leaving."

"No, that's not it…"

Qing's answer was difficult because it wasn't wrong.

In the end, if she had to accept it anyway, she decided to agree cheerfully.

"Hehe. I don't know. I guess I'll sleep when I'm dead."

"Excellent. Yes. I have been pondering how my disciple will achieve her progressed cultivation. It seems that although you easily understand martial arts, you do not contemplate their depths, so your attainments are delayed."

She only understood to the extent that someone explained, but she made no progress in pioneering her own martial studies based on that knowledge.

It was an accurate assessment.

However, even her good understanding was due to the shortcut of directly engraving it in her head using the Martial Arts Window, so how much worse would in-depth study be?

"Didn't I tell you before that your Sword Art of the Yue Maiden follows the principle of the Golden Mean of Jiutian Xuannü? It was a top-class sword art that encompassed all subtleties from the beginning, so it is only natural that you are blindly wandering now."

Ximen Surin unfolded her full-fledged teaching.

"The Golden Mean means nothing is excessive, so it encompasses all four basic subtleties of martial arts. These come from the harmony of Heaven and Earth, Yin and Yang: Swift, Dull, Illusory, and Heavy."

Swift Sword is a fast sword, and Dull Sword is a slow sword.

Qing raised her hand to ask a question.

"Uh, then isn't a fast sword always better? And since force comes from speed and weight, isn't a fast sword ultimately stronger…"

"Dull does not refer to slow speed. Dullness implies a lack of moving, so it is static. Swift is moving. Thus, the harmony of these two forms Yin and Yang, followed by the four aspects of Movement Within Movement, Movement Within Stillness, Stillness Within Movement, and Stillness Within Stillness."

"Um…"

Qing's eyes spun in circles.

Ximen Surin chuckled and explained.

Swift and dull could be typically exemplified by the contrast between Diancang and Wudang.

The martial arts of the Diancang Sect were the epitome of extreme speed.

The sword technique that pierced the sun was a beam of light that advanced like lightning towards the enemy's heart.

On the other hand, the martial arts of the Wudang Sect were about calmly holding one's ground.

No matter what vicious killing movements swirled towards them, they simply returned it with the principle of Tai Chi, never wavering like Mount Tai.

"Uh, hmm. I think I understand…"

Ximen Surin smiled gently at this.

"If you understood, wouldn't you have already reached enlightenment? For now, just engrave it in your mind. And then there are the subtleties of Illusory and Heavy."

Illusory Sword was also called Transformation Sword, focusing on confusing the enemy with dazzling and intricate sword energy emissions.

In contrast, Heavy Sword pursued a single, stubborn, and weighty strike that cut off the breath of life, sending the enemy to Sukhavati.

This could be exemplified by the contrast between Mount Hua and Shaolin.

The martial arts of the Mount Hua Sect were full of vitality.

The Sword Dance that depicted the petals of fully bloomed plum blossoms was in fact a real illusion of all those falling flowers and also the very essence of unpredictable change.

Shaolin's martial arts were straightforward.

While the martial arts of Shaolin Monks who kept the precept of "No Killing" did not contain deadly killing intent, they embodied the subtlety of heaviness in seeking to subdue the enemy with a single strike.

"The subtlety of the Golden Mean that embraces everything must contain all these subtleties, so one must understand all principles."

"Ah…"

And only then did Ximen Surin speak again.

"It seems my disciple has a talent for picking up martial arts from somewhere, so I am warning you just in case. Make sure to engrave this in your heart."

At this point, even Ximen Surin should naturally know.

Where on earth would she even pick up the Yijin Cleansing Method and Great Meditation Divine Arts?

Of course, seeing how she also picked up the Wave-Treading Subtle Steps, it was clear her connections were not ordinary, but those two Divine Arts were too much.

"Ah."

"It is difficult to understand the four basic principles with just one sword technique like the Sword Art of the Yue Maiden. Because it is balanced, no single subtlety stands out, and because nothing stands out, it is even harder to feel. So, if you learn martial arts that extremely pursue one subtlety each, and there are four of them, would you not understand them all?"

"Uh, you mean…"

"Swift. The fastest sword under heaven. This would undoubtedly be the Sun-Piercing Sword Technique of Diancang."

Dull. The most static sword under heaven.

This was what the Emperor Sword Form of the Nan'gong Clan, the Greatest Sword Clan Under Heaven, pursued.

Illusory. The most unpredictable sword under heaven.

This would be the Wisdom Sword of Tai Chi, a divine technique where humans overturn heaven and earth through the infinite changes of Yin, Yang, and Tai Chi.

Of course, some might mention Mount Hua's Plum Blossom Sword, but while it was flashy and unpredictable, it could be said to be shallow in depth, as light as flower petals.

Heavy, the heaviest sword under heaven.

"Hmm. If we're talking about martial arts that pursue extreme heaviness, there is not really a suitable sword technique. If anything, the Primordial Thunderbolt Dao of the Peng Clan could be called the heaviest Dao Technique under heaven."

"Then?"

Ximen Surin continued with a smile.

"Even if it is not necessarily a Dao Technique, doesn't my disciple already hold the subtlety of heaviness in her hand?"

"Ah! Then the White Hand Demonic Arts is- Ack!!"

Qing rolled on the floor again.

A moment later, she protested with eyes full of tears.

"I was just joking…"

"My disciple's jokes do not sound like jokes at all. And no matter if it is a joke, one shouldn't carelessly mention the name of Demonic Arts."

"Yes. So, I mean, the Buddha's Palm…"

It was a martial art that imitated the palm of Buddha, so it was truly a martial study that embodied the heaviest Imagery in the world.

Qing's lips protruded by three feet, having learned her lesson for carelessly making a joke.

"Then, which one should I learn first among them? It will take a long time to learn three of them."

"If that is the case, wouldn't it be best to first learn the Wisdom Sword of Tai Chi, which has both the subtleties of Illusory and Dull? The subtlety of Swift is the most common in martial arts even without the Sun-Piercing, so it can be postponed to the very end."

"So I should learn the Wisdom Sword of Tai Chi, Emperor Sword Form, and Sun-Piercing Sword Technique in that order."

At this point, she was stating it so shamelessly that there was clearly no intention to hide her cheats at all.

However, Ximen Surin had already noticed and essentially said she wouldn't ask about it.

So, Qing could also ask with a light heart.

"Hmm. If it's going to take some time, it might be good to learn the Emperor Sword Form first. There's something left by the Celestial Martial Emperor on the Absolute Sword Wall, so it might be better to learn the Nan'gong's martial arts before the Nine Sects' martial arts."

"Then I should learn in the order of Emperor Sword Form, Wisdom Sword of Tai Chi, and Sun-Piercing Sword Technique, right?"

"Yes. If possible, that is. Of course, this is no different from stealing other sects' martial arts. You probably will not be able to learn them, but even if you do, you must never use them carelessly."

If someone had heard this, they would have pointed fingers saying she should know better.

A master advising her disciple to steal others' martial arts and even listing them out?

However, Ximen Surin was already someone who had given up on the concept of human sentiment for her disciple since last year.

But looking at Qing's current state, one could say she had only arbitrarily discarded human sentiment without gaining anything.

After all, she had lost her sense of shame just to quickly gain a Protective Mirror that she would naturally realize and master as her realm increased. Looking at the results, couldn't this be considered a great loss?