\chapter{Xi-Mung Qing (6)}

Qing was not one to delay once she set her mind to something.

In a positive light, one could say she has good initiative.

It was a nice way of describing someone impulsive, careless, and impatient as having good initiative.

That night, she exchanged 3,000 Points for the Emperor Sword Form, raised it to Six Stars for good performance relative to Practice Points, and raised the Wave-Treading Subtle Steps to Twelve Stars.

However, how effective that Twelve Stars was…

Originally, Twelve Stars meant the Grand Star, a stage where one had not only mastered the martial art but also completely melted it down in their own way, completing their own interpretation on top of the existing Imagery.

However, all Qing's Martial Arts Window could do was stay faithful to its original function.

Ten Stars if all basic movements were crammed in, Eleven Stars if hidden movements were unlocked, and Twelve Stars if the unique effects (mostly large amounts of stats) that each martial art possessed were granted.

It was Twelve Stars only by Qing's standards in the world. As such, in reality, it was no Grand Star but just an ultra-cramming memorization trick.

Still, her abilities did surpass human limits.

In fact, at this point, she was tough enough that even if she fell straight down from a fairly high cliff with her bare body, she would only get a few scratches.

Then she would dust herself off, get up, pretend to be in a bad mood once, then stick her elbows back into the cliff and climb right back up, feeling refreshed as if she had just had a good workout. That was the level of monstrous strength and stamina she had attained.

Moreover, she kept getting stronger even after surpassing human limits.

In fact, at this point, one might question whether she even needed martial arts when she herself was strength incarnate.

Perhaps that was why she might still be stuck in the Late Stage Peak Realm.

Of course, Qing might feel wronged.

If one were to ask how she could be in such a state after learning so many great Divine Arts… Well, just because you had the best-verified textbooks didn't mean you would automatically study well.

While it was difficult to reach enlightenment with third-rate martial arts and poor textbooks, having good textbooks didn't necessarily mean your grades would skyrocket. Wasn't it all dependent on one's aptitude for study and attitude?

But Qing was a person from the modern era with military experience, as well as a world-class beauty who wonders why martial arts are even considered a form of study.

For someone who started from scratch and was now in her fourth year, just one month away from completing four full years in this Wulin journey, to have caught up to the Peak Realm through pure enlightenment was actually praiseworthy. She deserved nothing but accolades and compliments for her efforts.

Especially since she did not have a special forces background and didn't even bother to memorize a single Taekwondo form in the military, being just an ordinary social science major.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The swords of the Divine Maiden Sect were elegant.

Their father was the Yan Emperor, an extremely ancient, mythical-level conservative father among fathers.

The sword technique passed down by such a Yan Emperor to his daughter wouldn't have allowed for wild boar-like frolicking.

The Yanji Protective Sword, created in imitation of that Imagery, draws beautiful flows where even the slightest changes within the embrace of its lightly wielded sword strikes are splendid and elegant.

In fact, the Yanji Protective Sword just had a Gold Border by the Martial Arts Window's standards.

However, even Gold alone was enough to be called a great martial study worthy of being called a Divine Art.

When a Profound Realm Master who has achieved Grand Star wields such an ascending Sword Art, it's simply deadly for the opponent.

Ximen Surin's Yanji Protective Sword, reinterpreted at the Grand Star level, was not flashy.

Instead, it filled that empty space with the subtlety of the Heavy Sword, making it elegant and refined yet properly stubborn, containing an awe-inspiring force that made one's hair stand on end.

A vicious Sword Qi that couldn't possibly be imagined from a wooden practice sword without a blade gently curved and surged towards Qing's waist.

The sword tip, undulating up and down, could extend in either direction from that change, as if a single sword was approaching to target the head, body, and legs simultaneously.

At that moment, Qing's form showed a strange movement.

She stretched out her arm, swinging it while her feet showed a light movement left and right, and then, as if she were an incorporeal soul, she pierced through the sword's trajectory and appeared five steps behind Ximen Surin.\footnote{And here we get why the chapter title referred to Mungtaengi meme}

Ximen Surin turned around smoothly, extending her sword trajectory in a dot with an unhurried, demure posture.

Rather, Qing panicked and moved her feet again to the single point rushing towards her lower back, leaving pleasant afterimages dot by dot as she ended up standing with her back to her master far to the west.

Ximen Surin withdrew her sword and looked at Qing.

Qing scratched her head awkwardly.

"I guess I should only use this for running away."

"Indeed, it seems so."

Ximen Surin nodded as well.

They said learning the Greatest Footwork Under Heaven meant one would never be defeated, and it truly was unparalleled only in not being defeated.

While performing the footwork, one couldn't even breathe freely and had to follow the set order precisely, resulting in always appearing with one's back to the enemy in one of the sixty-four directions that were divided into eight directions of eight directions.

If the direction of the foot were to be even slightly off while performing the Wave-Treading Subtle Steps, one would trip over their own feet and fall with a crash.

There had been countless attempts to apply the Wave-Treading Subtle Steps to attacks, but they all ended in vain.

This was a characteristic that appeared because it was more of a Formation stepped on by feet rather than just footwork.

So it was a footwork only useful for escaping and avoiding battle.

However, wasn't it precisely because of this that it could be called a peerless Divine Art?

If one could escape with their body intact, it literally meant never being defeated.

However, it wasn't without weaknesses.

An enemy who properly understood the Formation could block the sixty-four changes of the Eight Trigrams Eight Palaces in advance.

Even without that, it was also vulnerable to attacks that filled the entire space or blind sword strikes that didn't rely on sight.

"Still, it is undoubtedly excellent for self-defense."

Ximen Surin's teachings were generally like this.

She opened the way for Qing to develop on her own by applying the martial arts she knew in her head as much as possible.

So Qing's daily routine involved rolling around and sparring diligently while the sun was up, then resting a bit after dinner while playing the flute.

Since everyone around her gave such enthusiastic support, saying she was so good, so pretty, the best, the flute that she never played outside became quite an enjoyable hobby inside.

Then she would return, light a lamp, open her books, and diligently copy until late at night, only going to bed when it was deep into the night.

Still, the Senior Disciples' special cotton-padded quilt made by sewing two blankets together did its job well.

She would spread it on the floor, lie down at the edge, grab the blanket, and then roll herself up tightly.

This way, it functioned as both a mattress and a blanket, soft underneath and blocking the wind from all sides.

Even in a cold room without windows or doors, one blanket was enough to create a soft and cozy bed.

Originally, Qing preferred to have her face and hands outside the blanket, but since there was not just a draft but a typhoon blowing in the room, this was better even if it was stuffy.

Additionally, there was a positive effect that Qing didn't know about.

After sleeping in that attention position for a day or two, her habit of tossing and turning in her sleep gradually changed to a corpse-like stillness.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The books she had finished copying piled up one by one, already exceeding half.

It felt like yesterday that she had eaten her fill of mooncakes for the New Year, but more than twenty days had already passed since then.

The cold had now reached its peak, so while her body's health remained the same, Qing's expression became desolate due to the sharply dropped perceived temperature.

At this, Tang Lan-ah subtly brought up the topic.

"Hey, Qing'er. Um."

"What?"

"I was thinking, how about staying at your place for a day? I've always wanted to sleep over at a friend's house…"

It had been a long time since Qing had refused to sleep in the same bed after being caught fondling her chest back at the Tang Clan.

However, Qing unexpectedly agreed readily.

"Oh? Really? Then come at night."

"Really?"

"Sure. You might want to sleep over at a friend's house once."

A smile appeared on Qing's face as she answered like that.

Tang Lan-ah was momentarily dazed.

\textit{What's this, why is she so pretty…}

It was understandable for her to think so since the girl who had been shivering with a sad expression all this time finally showed a bright face after so long.

And so, Tang Lan-ah received the promise and, for whatever reason, even took a short nap right after dinner, heading towards Qing's thatched cottage in a fresh state.

By the way, is this a house or an abandoned building?

There wasn't a single window or door, and the only household items were a desk, scriptures piled in the corner, and a bundle of clothes roughly thrown together and tied up.

Qing, who had been diligently filling in her copying, no, transcribing scriptures, greeted Tang Lan-ah with a somewhat evil smile.

"I don't have much to offer. Want some cold water?"

"In this cold weather…?"

"I'm too lazy to chop wood, so there's no firewood."

Qing's state of undress was just due to Ximen Surin's resentment, so in fact, she could have lit a fire if she wanted to without much issue.

In the Divine Maiden Sect, the principle was to gather firewood on one's own.

It wasn't about cutting just any tree, but the rule was to go all the way down the mountain to the gate at the foot of the mountain to cut wood.

Most of the sightings of the Fairy of Mount Wu were actually due to disciples who had briefly gone down to gather firewood.

She didn't want to go all the way down the mountain and back just for firewood, and she couldn't steal the disciples' fuel wood given her position of respect.

Besides, if it's cold, why not just wrap up in a blanket?

"Let's sleep, I'm sleepy. Let's sleep."

Qing said as she spread out the blanket.

However, that was the only one that existed. Just that one blanket.

"Huh? Is that all? What about pillows…?"

"There's no such thing. My place is humble, so this is how it is."

And then they lay down side by side, pulling the opposite end of the blanket to cover themselves.

"…C-Cold."

"Cold? Wear warm clothes."

"No, th-this is unb-bearable, it's s-so c-cold."

Tang Lan-ah's body shook violently.

It's cold!

It was a space with no warmth in the middle of winter, with a huge draft hole and only a roof.

If you stick your head out, it's so cold that it's painful as if your eyes might freeze, and if you put your head inside, you can't see anything, it's stuffy, and you can't breathe.

Yet the inside of the blanket isn't particularly warm either.

If Tang Lan-ah thought she could smile and get through the cold of a mountaintop with bitter winds blowing on a midwinter night with just one blanket, she would have to be Xue Lan-ah, the Ice Flower rather than the Poison Flower, a woman from that far Northern Sea.

"Th-this doesn't s-seem r-right."

"Then there's nothing we can do. I can't see you off looking like this, though."

And so Tang Lan-ah shuddered and ran away.

\textit{No wonder she agreed so readily.}

\textit{But is it really okay to live like that?}

\textit{Is there some Northern Sea blood mixed in her family line?}

\textit{Alright, this time I was underprepared.}

Tang Lan-ah cleanly admitted defeat.

However, the famous Sichuan's Most Wicked Woman, the Speaking Poison Flower, was also persistent.

Next time, she would wear four layers of thick clothing, a fur hat that covers her ears, and even a face mask, she decided, vowing to prepare each item right away.

Of course, doing so might overcome the cold.

But wouldn't that make her look like a robber coming to steal rather than a friend visiting?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ximen Surin received a letter.

It was a letter stamped with the official seal of the Wulin Alliance.

The letter, which began with 'To the respected Senior Ximen', conveyed news about the Demonic Cult's unilateral request for reconciliation and other Jianghu news that was varied but uniformly unpleasant, such as the annihilation of the Yun Clan of the Jin Prefecture and the rampaging of mysterious new bandit groups.

And at the end, it wrote the conclusion.

And what it said was:

\begin{quote}
[Therefore, we wish to hold a grand conference to unite the Orthodox Wulin in these chaotic times, and we would be grateful if you could attend and grace us with your presence.]
\end{quote}