\chapter{Xi-Mung Qing (2)}

Indeed, there had never been such a major incident.

To think her disciple had the Heavenly Demon.

Wasn't this the evil spirit under heaven that had invaded Zhongyuan four times, turning the entire world into a house of mourning?

She might have to officially register her in the Divine Maiden Sect.

Should she take her to the Grand Elder Hall on Divine Maiden Peak and make her read Daoist scriptures until she dies of old age?

Ximen Surin seriously pondered.

Her foolish disciple had embraced the source of calamity for all under heaven, so the disciple's lack of virtue was the master's lack of virtue, and since this was all due to having an incompetent master, perhaps she should keep her by her side for life.

"You insufficient wench. You just had to get yourself out safely. Why on earth did you take such a monstrosity? How do you expect those Demonic Cult bastards to let you go like this?"

"But… if I had just escaped alone, wouldn't those Demonic Cult bastards come rushing in again…"

"What, did you have such an impertinent thought that you should sacrifice yourself for the peace of all under heaven?"

"As if I knew this would happen. And rather than all under heaven or whatever, it's because the war would reach our family at the Divine Maiden Sect too…"

How could Ximen Surin be angry in front of a disciple who spoke like that?

Ximen Surin let out a deep sigh.

\textit{Wanting to keep her by my side is just my own greed.}

\textit{It's this master who is happy to see her every day, so I'm trying to keep her close with a plausible excuse.}

"So, it seems you headed to Sichuan after subduing the Heavenly Demon Spirit and leaving, but what is this treason business? And who is that bastard who split my disciple's breast. The one who deserves to be torn apart?"

"Ah. The Embroidered Uniform Guard Assistant Commissioner? It was some high-ranking bastard like that. This disciple already put him to death, though? But that guy was… Yeah, that's right. A Reinforced Blood Demonic Human? Something like that."

Ximen Surin frowned.

It seems every time her disciple opened her mouth, something substantial came out.

An Assistant Commissioner refers to the third rank in the government's military organizationa hierarchy, so an Embroidered Uniform Guard Assistant Commissioner would mean the Guard Assistant Commander.

What did it mean that a top-ranking military official qualified to directly hold the Imperial Banner was a cursed Demonic Human who had undergone the Blood Cult's ritual of human sacrifice?

It was a sensitive matter that could be considered treason just by mentioning it.

"I should tell you the story from when this disciple arrived in Sichuan. This disciple wanted to eat malatang, ah, the Greatest Chef Under Heaven, that's right, Master, there's a Greatest Chef Under Heaven in Sichuan, but he's not really the Greatest Chef Under Heaven, he's the Greatest Chef in Sichuan, but since Sichuan cuisine is the greatest cuisine under heaven, he's called the Greatest Chef Under Heaven instead of the Greatest Chef in Sichuan, anyway, so there's this ultimate malatang… Ah, I ended up not eating it. Master, do you like malatang by any chance?"

"…? I do not enjoy such heavy, numbing food, so I do not eat it. Regardless of malatang or whatever it is, just move on."

"Ah. Anyway, these guys called the Five Poison Sect. Ah. What was with that Five Poison Sect again? Did we just happen to overlap by bad luck? What happened again?"

The Five Poison Sect had backed the wrong horse with the Eastern Depot Eunuch, so they were soon to receive a severe attack from the royal household's eccentrics and the Tang Clan's avengers.

Qing didn't know because she didn't care, and she didn't particularly want to know either, so she just explained roughly and moved on.

"…And when I woke up after sleeping like that, they said it was all over."

"I see. You kept your loyalty to the end but did not dig too deep. For once, your conduct was quite excellent. If only you had not gotten hurt, it would have been perfect."

"Ah, that's right. Master, look at this, doesn't the cross-shaped scar have a kind of wild charm- Ack!"

SMACK!!

Qing, who dared to show off her unnecessarily large breasts in front of her master, rolled on the floor.

"You are truly asking for a beating."

"No, wait, it really hurts…"

"You say it hurts, but your endurance is growing. My goodness. If I dare speak, even cold iron would not be harder than my disciple's head."

This time, she was serious.

She said she had learned the Yijin Cleansing Method.

She never imagined that its mystical effects would create an iron, no, a cold iron head.

Ximen Surin, who was about to tell her to leave the scar on her chest as a lifelong lesson, changed her mind.

\textit{There are some who don't learn from lessons.}

\textit{This insufficient wench was cheerfully talking about wild charm even with a hideous mark carved on her chest.}

\textit{Even if she told her to keep it as a lesson, it would only remain as a flaw for others to gossip about.}

"Let us go home for now. The news has been such that your fellow disciples are worried beyond measure."

From what she heard, there was nothing good about staying at the Tang Clan any longer.

Since she was involved in the Imperial Family's power struggle, it would be better to hide away from the secular world until her name settled down a bit.

Qing rolled her eyes and answered quietly.

"Uh, I have to wait for Sister Wannabe…"

"Tell that old man left in front to set up house in Zigui later. Even if he is a servant, we cannot bring him into the sect anyway, can we?"

Zigui was the name of a city near the Divine Maiden Sect.

The Divine Maiden Sect was a sacred realm where men were forbidden.

At least, it had been so since the Celestial Martial Emperor; before that, there had been a few invasions by those outrageous Imperial Family bastards.

Since the Divine Maiden of Mount Wu enshrined in the Daoist temple was the daughter of the Yan Emperor and the lover of the Yellow Emperor, they had reluctantly let it slide. However, after the government's power completely deflated, they never allowed it again.

In other words, it had never happened in Ximen Surin's lifetime.

"Uh, the scar treatment… Ah. Well, I guess that doesn't really matter."

"We can just bring medicine for the scar. Isn't the Tang Clan's Sore Rejuvenation Powder famous for its effectiveness?"

"Oing? You mean we could have just applied medicine?"

"Of course? Did you think you had to rub and knead the troublesome wound until it got worse?"

"She definitely said it was An Mo. It wasn't exactly kneading, but she stroked and stuff…"

An Mo. Also called massage for short, it referred to the Chinese people's healing technique.

It was also a primitive medical practice that naturally arose in various parts of the world, not just among the Chinese people.

"An Mo is for muscles, tendons, and bones. What use is there in kneading flesh? It is already heavy and large enough to ruin the drape of clothes, so do not even think about touching it. It might get even bigger."

Qing's eyes narrowed.

\textit{That Tang Lan-ah is quite a wicked woman, wasn't she?}

\textit{Shouldn't her medical license be revoked?}

Of course, there were no separate licenses in Zhongyuan, and the uncivilized Chinese didn't recognize female physicians, so she was just a physician wannabe who couldn't be called a physician.

Knock knock.

As they say, speak of the devil and he shall appear; Tang Lan-ah appeared right on cue, knocking on the door.

"Lunch is ready. Would the Godmother perhaps grace us with her presence?"

Tang Lan-ah nervously fidgeted as she invited them to the meal.

Yet her eyes sparkled, fixed on Ximen Surin and unable to leave.

This was because the Godmother Ximen Surin was the idol of all female martial artists in Jianghu.

How could a female martial artist not be nervous and excited upon meeting the Zenith Among Women?

Qing pointed at her, saying she had met a good person.

"Hey. You. Is it okay for a physician to deceive a patient?"

"Huh? Who? Me?"

"Yes, you."

However, this was an unjust accusation for Tang Lan-ah.

While she couldn't say she had no personal interest, it was a medical procedure to properly align the internal tissues that had been completely split in half.

Moreover, she had been focusing all her mental energy and even using her Inner Qi in her utterly devoted care, sweating profusely and exhausting herself each time.

Ximen Surin wasn't a physician either, so her knowledge of treatment methods was limited to sewing up cuts, setting broken bones, wiping blood, and applying medicine.

She didn't really know proper medical techniques.

"…Sorry. I didn't know."

"Hmph. Sorry for being a quack."

"I'm really sorry."

"Oh? If you're sorry. Ahem. You have to grant my request later. You have to grant as much as you're sorry."

Not just a few, but as much as she's sorry?

It was truly a vicious way of speaking.

As the not-so-docile Qing was about to argue that there was no such thing, Tang Lan-ah had already turned her attention to Ximen Surin and spoke demurely.

"Great Expert Ximen, I have a request. Would you allow this humble one to stay at the Divine Maiden Sect to take care of Qing'er's wound and check her pulse?"

"If you would do that, I would be grateful."

Ximen Surin looked around the luxurious guest room.

The Divine Maiden Sect practiced frugality in all aspects of life, with meals being the only exception.

"Our sect's lifestyle is frugal and might be quite arduous for you. Would that be alright?"

"Of course! Rather, I would love it! Thank you!"

Even if she wasn't her disciple's friend, Ximen Surin would evaluate Tang Lan-ah quite favorably, at least for now, because she was a female physician.

Wasn't it true that there were no female physicians in Jianghu, making it difficult for women to seek medical attention for embarrassing symptoms?

She thought that rumors couldn't be trusted, as she had heard that Tang Lan-ah was a childish brat who threw tantrums and knew how to make a fuss.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After receiving lunch hospitality, Ximen Surin immediately packed her bags and left the Tang Clan.

And only then did Ximen Surin turn her eyes to look at Cui Liweng.

Cui Liweng couldn't meet her eyes and only looked at the floor.

With nothing to his advantage in terms of martial prowess, age, or even his relationship with Qing, he could only meekly shrink and await his fate.

Ximen Surin glimpsed his anxious inner thoughts.

The Purple Lightning Demonic Warlord was a somewhat infamous figure as the Demonic Cult's patrol lion.

It seems he at least knows to be ashamed of his past.

Still, it was an unimaginable emptiness to have scattered one's lifelong achievements.

Although her disciple had taken his side and likely added a rather biased interpretation of what happened, if he had passed on his Divine Arts after the dissolution of his Inner Qi…

Ximen Surin finally let out a deep sigh and spoke.

"Because my disciple is lacking, her going out into Jianghu is always like leaving a child by the water's edge, so I am never at ease. At such times, please look after her a bit."

"…Yes. Thank you. Senior."

"Hmph."

It was truly frustrating to be called Senior by a Great Demonic Adept due to having a wayward disciple.

Still, if a master of the Unrestrained Realm was going to take care of her disciple, it was something she could endure to that extent.

Her disciple's journey in Jianghu had to be quite extraordinary.

Perhaps it was an ordeal following her rejection of her innate killing nature, so she couldn't forcibly confine and stop her either.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Grand Prince Dexian, pacing in the royal household's courtyard, asked Hag Yan, who wore a sly smile.

"Hmm, wouldn't it be alright to at least see them off?"

"Your Highness, it's best to just stay out of sight. She might look like that now, but she used to be the crazy bitch called the Female Mad Dog. Does Your Highness think the Grand Sect Leader of the women-only Divine Maiden Sect, who even passed on her surname to her named disciple, would stand by and watch her enter someone else's household?"

"No, who said anything about taking her into the household? I just meant to see off a friend, that's all."

"Oh my, Your Highness. You should know when to hold back. Later, after things are done and set, you can just ask for forgiveness. Do you think she would dare to lay a hand on her son-in-law, who sits on the Dragon Throne?"

Hag Yan said with a grinning face.

"No, what do you mean son-in-law? I'm not…"

"Are you not? Didn't you ask this old woman about measures for harmony between the government and Wulin?"

"Well, that was for the greater good…"

Grand Prince Dexian made excuses with a reddened face.

Hag Yan, having caught a rare opportunity, kept teasing him like a grandmother teasing her grandson, as was her specialty.

"The greater good, yes, that's nice. This old woman likes the greater good, but she also likes personal interests too. I've lived well liking everything up to now, so if Your Highness likes it, this old woman likes it too. Hehehe."

And in fact, this was the biggest problem with those who claimed to have the blood of the Son of Heaven.

They think that just by flashing a purple background with a golden dragon pattern, everyone in the world will go crazy and rush over.

Shouldn't one first ask if the wine seller is open for business before worrying about what to drink?

There's no use in gulping down bowls of honey water to protect your stomach before the wine table; it will only bloat you unnecessarily.

