\chapter{Xi-Mung Qing (4)}

Anyway, she sent the little squirt away to train, and led Tang Lan-ah towards the Sect Leader's Hall.

The current Sect Leader, Wang Zhuxi of the Heavenly Muted Sword, was a woman with a particularly weak presence.

This was partly due to being overshadowed by the Grand Sect Leader Ximen Surin, who shone so brightly.

But according to what the Senior Sisters said (Qing was the youngest Junior Sister in the Sect Leader's allocation), the Great Senior Sister had always been characterized by a faint presence that seemed to be there yet not there.

So much so that her title was the Heavenly Muted Sword; it came from a single move where she had pierced the heart of the past's Public Enemy of Wulin, the Ravenous Sex Fiend, from behind without even her allies noticing during the subjugation.

"Yes. It is truly admirable and excellent that you learned medical arts at such a young age. Since you've come all the way to our Daoist temple, receive plenty of pure energy. There are no particular set rules, so rest comfortably at ease."

"Yes, Elder Sect Leader."

"Hmm. A female physician, what a wonderful sound that has. Of course, I do not mean anything else by it, but you came to check on our youngest sister's injury prognosis, yes? How lovely of you to be so thoughtful."

"Ah, no. Please withdraw your words."

"Yes. You should rest well. Rest, indeed. Rest very well."

As she particularly emphasized resting well, Tang Lan-ah, who had been sweating profusely, quietly spoke up.

"If you would allow it, though this humble one's skills are still lacking, could I perhaps check pulses while I'm staying here…"

"Oh my. How admirable. So that beautiful appearance comes from such a kind heart."

And so the Sect Leader achieved what she wanted.

After that, when they were about to prepare bedding for a room in the guest quarters, Tang Lan-ah couldn't hide her surprise.

"What's this? It's empty?"

"This is your room, though?"

"…?"

"…?"

Tang Lan-ah clapped her hands as if she understood.

"Come on, don't tease me for not having Jianghu experience. You even told me to take off my shoes when getting on the boat. Do you think I'll fall for it again? How can this be a guest room when there's not even a bed?"

"Then what am I holding?"

"A blanket and a thick blanket?"

"This is called a Yo. It's used for sleeping on the floor."

"Gasp! Is this that thing I've only heard rumors about…!"

The daughter of Sichuan's richest family seemed unable to accept reality and was in shock.

Well, the size of the room was only slightly smaller or similar to Tang Lan-ah's ultra-luxurious bed, so what could one say?

"Isn't this extremely hard?"

"Hard? Try lying down once, then."

Qing spread out the thick yo with her monstrous strength in one go, laying it out with a swish.

Tang Lan-ah lay down on it with an excited, heart-fluttering expression.

Then her expression immediately hardened.

"It is hard!"

"I didn't say it wasn't, did I? Of course it's hard."

"No, how can anyone sleep on this?"

Tang Lan-ah made a tearful face.

Qing snorted.

Last winter, Qing had fallen asleep crouched in a corner, unable to even lie down due to the cold, shivering without even a single blanket.

Even then, she couldn't lean against the wall because it was cold.

"I'll specially bring you two more. Won't three layers be more or less okay?"

"Hmph. It's uncomfortable."

"When you sleep outdoors, you just have to remove the pebbles and lie down, you know? You're talking nonsense."

Tang Lan-ah looked at Qing with an aggrieved expression.

These words coming from someone who spent more than half the day sprawled out comfortably on a bed didn't feel convincing at all.

"Then you, you're a Great Senior Sister. Aren't you using a nice room all to yourself?"

"What, do you want to see my house?"

And so Qing revealed her sweet home that she had been dreaming of.

Qing's feelings upon seeing her home after so long were truly, well, very shabby.

\textit{…Was it this small?}

\textit{Did someone sneakily eat away at it and shrink it?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ximen Surin had many worries.

It was because of the disciple she had taken in her twilight years.

How on earth was she supposed to correct that unruly behavior?

Even last winter, with the mindset of whipping a crying child's calves even more, she had almost stripped her naked.

She had hoped that feeling shame from being nearly naked would make her reflect on her conduct, but instead, she ended up losing the very emotion of shame itself.

Even when beaten, it only lasted for that moment, and once the pain subsided, she would forget as if nothing had happened. A grown woman acting without dignity, having the audacity of being coquettish to a great elder of Daoism.

Of course, how could she not understand that heart that cared for a lonely-looking master?

She was only grateful for that kind nature.

If it weren't for that, she would have seriously considered having to deal with the calamity of the Heavenly Slaughter herself.

Still, thanks to that stubborn stupidity, she could have confidence that she would be able to overcome even in the face of that vicious fate of the Heavenly Slaughter.

In fact, Ximen Surin, while calling herself a master, hadn't particularly passed on any martial arts.

She had taught the Heart Cleanse Mirror of Zhu Xiang, and was shocked when her disciple immediately achieved the Grand Star and appeared.

However, for other martial arts like swordsmanship, she had judged that she needed to gain enlightenment from what she already possessed.

So the training method Ximen Surin had prepared for this winter was also an extension of that.

Thud. Thud. Thud. Thud.

Stacks of books piled high kept landing in front of Qing with heavy sounds.

"Uh, Master?"

"I pondered why my disciple's enlightenment has not come, and I thought perhaps it is because your knowledge is not just lacking, but completely non-existent."

It was a statement that outright called her 'You ignorant wench'.

"A girl who practices Daoist and Buddhist martial arts doesn't even know a single Daoist Immortal or Buddha, so how could you grasp enlightenment even if it came?"

"Uh. Studying at this age is a bit…"

"Learning is a lifelong journey, my disciple. I will not allow you to go out into Jianghu until you have copied all these books twice."

"Ah."

Qing made a tearful face.

Of course, the books of Zhongyuan were not like those in Qing's homeland with thin paper densely packed with text.

The paper was thick and the characters were as big as gates, so even if she diligently copied them, she might or might not see results by spring.

Well, it depended on Qing's sleeping hours.

Qing looked down at the books.

Just from the titles, she could tell they were Daoist and Buddhist scriptures.

Which meant that among books, they were the least interesting religious texts.

Moreover, the scriptures of this era were closer to philosophical texts in commentary form, where even the same passage could have different interpretations depending on the author.

In other words, they were not interesting.

Even a college entrance exam could not compare; let's say she had to start studying for one because the exam was the day after tomorrow. Even then, these books could never be interesting.

Qing responded with a grave expression.

"Master. I'd rather strip nak- Ack!"

SMACK!!

Qing rolled on the floor.

"Tsk tsk. No matter what, a young lady in her prime should know better than to say such things."

"Master, it seems to be getting stronger and stronger… At this rate, won't your disciple's head really split open?"

"Stop exaggerating."

"No, it really hurts…"

Qing said with tears welling up in her eyes.

Of course it hurt, since she was hit to make it hurt.

"Since my disciple knows no shame, stop saying nonsense and do as you're told. You may be ignorant, but you do have a brain, so you'll naturally memorize as you write."

"Yes…"

Qing answered dejectedly with slumped shoulders.

However, there was something that wise people throughout all times and regions unanimously said:

The mouth is the source of all evil, so always be careful with your words.

In fact, last winter's ignorant Protective Qi training was close to an outrageous act that would make all Masters in Jianghu point fingers and curse.

How could one bear the shame of exposing a grown female disciple half-naked in front of the sect disciples?

Even Ximen Surin had been apologetic and heartbroken throughout, but this was the result in the end.

Ximen Surin was human too.

She couldn't help but feel resentful in proportion to that heartache.

"But since my disciple has shown such great spirit as to dare mention undressing, how could I as a master stop her? It seems you haven't forgotten that training even after enduring such hardship all winter, so I shall allow that as well."

Qing realized that she had not only lost her original investment by carelessly opening her mouth, but even her capital had been completely wiped out.

Upon cleanly giving up, Qing voiced a single desperate hope.

"Then, could you please allow just one blanket this time? I want to sleep lying down…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Hey, Qing'er. We need to apply medicine."

When Tang Lan-ah occasionally called her by a different name than usual, she tended to look around awkwardly and shyly after speaking, as if something was so awkward and embarrassing.

This time too, Tang Lan-ah was about to look around when she immediately became shocked.

"KYAAAK, you, you, what kind of state are you in!"

Tang Lan-ah screamed, covering her eyes with both hands.

Her eyeballs were fully visible between her fingers, but since it was originally a pose meant to express a woman's embarrassment, there was no particular need to nitpick.

Qing answered with an enlightened expression.

"…This is how it turned out."

"Why is your house like this? Did thieves come?"

"Well. Something like that."

"Aren't you cold? The wind is blowing so fiercely…"

"I am cold…"

Being okay and being cold were two different things.

Just like getting hit with a nuclear noogie didn't cause injury or tearing, but that didn't mean it didn't hurt.

Still, it felt better than last year, subjectively.

\textit{Ah. Maybe it's because I'm at least wearing bandages…}

It was natural, given that she had learned the Blissful Maiden Arts that helped endure heat and cold, along with two Ice Arts.

Unless it was the winter of that far Northern Sea, this body wouldn't be invaded by the cold of Zhongyuan.

"Why, why are you in such an indecent state?"

"Training…"

"What kind of training is this? Are you perhaps being hated or bullied? How can you be in front of others like that…"

"They're family anyway…"

"This isn't a matter of family…"

Tang Lan-ah swallowed hard.

\textit{But, it's so lewd. How can a girl be so, so lewd?}

While dressed in an outfit that only the world's most lustful woman would wear, her expression and eyes were filled with gloomy resignation, shoulders slumped with a sad air.

\textit{That contrast is really, how should I put it, erotic…}

Tang Lan-ah just kept gulping like that.
