\chapter{Xi-Mung Qing (1)}

Ximen Surin's concern was indeed justified.

When Qing recovered dramatically from her madness at the Demonic Cult through the teachings of the Great Meditation Divine Arts, the ominous star in the sky had glowed red with anger and regret.

Ximen Surin, who read the meaning of this star, had offered ritual sacrifices in the middle of the night, relieved that her disciple had overcome a great crisis.

In fact, she had been worried a thousandfold since then, fearing that her gentle, kind, and not at all vicious disciple might return injured in body or mind from that ruthless place called Jianghu.

And as autumn deepened, the time for her return had passed, but the disciple did not come.

Then a disciple who went out shopping brought news asking about rumors of a great calamity in Sichuan, something about rebellion and assassination plots, with Qing's name involved.

With her heart sinking, Ximen Surin arrived in Chengdu in one step, crossing the natural barrier of high mountains in the Sichuan basin using the highly refined technique of Sword Flight.

Of course, Ximen Surin was a great elder of Daoism who knew courtesy and propriety, so she did not commit the uncivilized act of knocking on the Tang Clan's door in the middle of the night when she arrived.

She first got a room and spent the night. Then, after tidying her clothes, she visited the Tang Clan at the hour of Si (10 AM), when it would not be an inconvenience to visit.

And finally, she laid eyes on her disciple.

Despite it being the time when the sun was high in the sky and all under heaven were busy under the Yang Qi of the brightening sun, there was her disciple, sprawled out on a luxurious silk bed, wandering in dreamland.

Moreover, the shameless girl was almost naked, with only bandages on her chest, her limbs spread out with the blanket kicked off, a sight that would make anyone who saw it feel ashamed.

Ximen Surin's anger meter shot up.

As a Profound Realm master became angry, the very air vibrated, gravity doubled, and a pressure that crushed space emanated, just from that alone.

Under that pressure, the disciple gently opened her eyes, and as their gazes met, she burst into an innocent smile with an unfocused, dreamy expression.

"Hehe, it's Master… I missed you…"

And then she closed her eyes again, making soft breathing sounds.

Ximen Surin's anger meter, which had exceeded its limit, hesitated and gradually stabilized.

\textit{Right. It is fine as long as the child is safe.}

It is not like she is showing her sleeping appearance to anyone, so what does it matter if the scene is a bit ugly to look at, or perhaps even extremely ugly? 

Moreover, her face had become even more beautiful and younger in the time they hadn't seen each other, and her limbs had grown longer, clearly having undergone a transformation.

It was disappointing that she hadn't reached the Transcendent Realm, but in fact, it was quite common for one's realm to remain the same while only the body changed if one failed to grasp enlightenment and lost it.

Such lost enlightenment was bound to come again soon, so there was no need to be disappointed.

\textit{But why was she wearing bandages only on her chest?}

Although there were no bloodstains or scent of blood, the fragrant smell of medicine made Ximen Surin's heart sink.

As Ximen Surin reached out her hand, the bandage on Qing's chest gently pulled down, revealing what was inside.

There, an ugly wound sewn with thread was exposed!

It was a terrible trajectory that would have cut through her ribs if it had been just a bit deeper, and even her heart if it had been deeper still.

Thinking the child might be lying down after taking medicine because she was in pain, she quickly approached to check her pulse, only to find healthy meridians that had developed into a difference of heaven and earth compared to before, and traces of numerous Demonic Arts…

Ximen Surin's anger meter instantly shot up and exploded through the ceiling.

"YOU-LITTLE-WENCH!"

SMACK!!!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

With tears welling up inside both eyelids and a bump protruding from one corner of her head, Qing knelt on the floor with both hands raised high.

"You wench, you have been rolling your body around recklessly and got yourself a huge gash. How admirable. How so very admirable."

"Well, they said the scar wouldn't remain…"

"Haa? You are even bragging about it, I see. Then, what about all that Demonic Qi patched up inside you? Will the Demonic Arts disappear without a trace later too?"

"No, that's not it…"

"That's not it?"

"Hehe. This disciple greets Master. I missed you. A lot."

Qing naturally bent her upper body and made a grand bow while keeping her hands raised.

Ximen Surin, having achieved Body Reconstruction at a high level, only had the appearance of a noble lady, but in reality, she was a great senior of Wulin who had lived even longer than Cui Liweng.

Having lived that long, she knew that the greeting Qing was offering was not just an act to avoid the current situation.

Rather, it was filled with sincere longing, so the resentment she had been feeling gradually melted away.

At this, Ximen Surin let out a deep sigh.

"You say you missed me, yet you were sprawled out living the good life in someone else's house?"

"They said they'd make sure no scar remains. I didn't want to worry you."

It was a statement that melted away the remaining resentment.

However, not wanting to forgive her right away, Ximen Surin spoke sharply for no reason.

"Ha. So you conspired to make a fool of a master who does not even know her disciple's chest was nearly split open."

"Hehe. Actually, my chest was already split ope- Ack!"

SMACK!!

Qing rolled on the floor.

Ack. She hit the same spot again!

A Profound Realm master's aim never wavers.

Moreover, it was practically a quantum entanglement super-flick that transcended distance, surpassing mere beating to deliver a strike.

Highly advanced martial arts even transcend science, after all.

Qing, who had been rubbing her head until it felt like it was on fire, saw Ximen Surin's fierce gaze and flinched, raising both hands again to assume the position.

"Haah. How is it that in my twilight years, I have a disciple who has nothing satisfactory about her except her nature?"

If hell existed and the numerous evil people burning there heard this, they would curse, saying she must have eaten through her asshole to reach her realm. After all, how could her way of thinking be so backwards and wrong?

"Fine. But what kind of Demonic Arts did you learn? I clearly warned you to stay away from them."

"Well, you see. This disciple didn't learn them because I wanted to…"

Even Qing's way of speaking resembled Tang Lan-ah's in front of Ximen Surin.

"If you did not learn them because you wanted to. Are you saying someone threatened you with a sword to learn Demonic Arts, as you put it?"

"Well, that's actually how it turned out…"

Ximen Surin's eye twitched.

\textit{Come to think of it, besides her nature, the disciple had a talent even more dazzling than her disposition.}

\textit{It wouldn't be strange if some Demonic Adept had set their eyes on her and made her learn Demonic Arts.}

\textit{But even so, it should have been just one.}

"No, which ill-mannered bastards took someone else's disciple and made her learn Demonic Arts? Don't tell me the Demonic Cult kidnapped you or something."

"Well, it's true that the Demonic Cult kidnapped me…"

Ximen Surin's expression became even more serious.

"The Demonic Cult? I see. Seeing that you are safe now, it seems you managed to escape somehow. More importantly, let us hear about what kind of Demonic Arts you learned. We need to know to deal with it, is that not so?"

"Oh. Well, first there's the Purple Lightning Demonic Arts and the Black Slaying Demonic Palm…"

In fact, the Demonic Cult would feel rather wronged here, as these two were the only Demonic Arts they had forced her to learn.

The rest were ones Qing had forcibly taken and learned herself.

"The One Hundred And Eight Asura Sword, Heavenly Ice Sura Demonic Arts, Blood Demon King Divine Arts, and the Lustful Immortal Disrobing Dance. That's about it, I think."

"…You learned quite a lot. My goodness, and you learned four of the Ten Great Demonic Arts Under Heaven. At this rate, you seem poised to collect all ten."

"But I learned good things too! The Yijin Cleansing Method and Great Meditation Divine Arts you mentioned, Master."

"Wait. No, wait."

Ximen Surin waved her hand.

The Demonic Arts had clear origins, and since she said she was kidnapped by the Demonic Cult, their despicable intention to brand her as a Demonic Human even if she escaped was obvious.

But the Yijin Cleansing Method? And the Great Meditation Divine Arts?

Was there a Shaolin monk and an Emei nun amicably captured in the Demonic Cult, and they happened to be owners of Divine Arts who passed them on?

"Hmm. Nevermind. I see. Well. What else?"

Ximen Surin's expression softened.

Her disciple had always been one to learn strange things when she went out into Jianghu.

She had guessed that there must be some means she couldn't speak of, so thinking about it now, even the initial question of what she should learn was extremely meaningful.

"The Supreme Yin Jade Maiden Divine Arts and the Blissful Maiden Arts. They said it was clearly a Daoist cultivation technique."

"Although it is a bit ominous, that is correct."

"Ah. And this was given to me as a gift, but I wasn't sure if I should learn it."

Qing took out the secret manual of the Wave-Treading Subtle Steps from the guest room's drawer and held it out.

Ximen Surin's expression hardened again as she roughly opened and skimmed through it.

It seemed today was a day when her facial muscles had no choice but to be hard at work.

"This. This is no ordinary thing."

"I think it's called the Wave-Treading Subtle Steps."

"Has the Chakra Witch settled in the Demonic Cult? Hmm? But it does not seem like you mentioned learning the Chakra Demonic Tribulation."

At this, Qing's expression was the one to answer.

And per usual, if Qing was unaware of something, anyone in the world could tell by looking at her face.

Ximen Surin changed her question.

"Was the person who gave you this in the Demonic Cult?"

"No. Someone in the Grand Prince's household gave it to me."

"I see. The royal household… Burn this after you have learned it. It is something that brings blood to the world."

"Ah. They said that too. Something about a bloodbath or whatever?"

"That is right. An entire sect was annihilated over this one book, so it is an object that people in the world covet that much."

The Blood Disaster of the Yunseng Sect. It was a common tragedy that occurred when someone without the power to protect it possessed a treasure.

"Oh, is it a good martial art?"

"It is said to be the Greatest Footwork Under Heaven. I hear that when mastered, its movements are like the wind, unable to be caught by anything in the world. Since it can preserve one's life even in the worst situations, it is a Divine Art that can indeed be called the greatest under heaven."

"Then, couldn't we just use it as our Divine Maiden Sect's technique? I've already memorized it all. We could just change the name to something like Divine Maiden Divine Steps."

Ximen Surin smiled benevolently.

To her disciple, even one of the greatest Divine Arts under heaven was just something nice to have if possible, and no big deal if not.

The problem was that she treated Demonic Arts the same way, not knowing how terrifying they were, which led to this situation.

But is there anything in the world made of just one side?

Yin and Yang. Shadows falling behind light. This was the principle of the world.

So perhaps this elderly's job was to cover the disciple's shadow with the master's shadow.

"Alright. Let us do that."

Ximen Surin put away the secret manual.

While she might not do this for other martial arts, since this could ensure her disciples' safety, it was worth enduring the vile act of stealing and overlaying the legacy of a vanished old sect.

"Ah. That is right. Let us hear your story. How did you escape from the lair of those evil Demonic Cult bastards?"

Because Ximen Surin's gaze was so warm, Qing's heart gradually melted and loosened.

But as always in front of her master, she loosened her guard a bit too much.

"Well, you see about that. Once again, this disciple crushed the Demonic Cult's ambitions with brilliant exploits. Ah! That's right. Look at this. Yap. Heavenly Demon, I choose you! Heavenly Demon Summon! This is the true form of this bastard called the Heavenly Demon. How it happened was…"

The Heavenly Demon Spirit rose from the palm of the chattering Qing.

At the same time, a vein also popped up on Ximen Surin's forehead.

And per such natural progression, it was time for something to pop up on Qing's crown as well.

Following that, SMACK!!!

The sound of a walnut cracking reverberated clearly across the pure heaven and earth beyond the room's door.

\begin{lstlisting}
	The chapter original title is 서뭉청/ 'Ximung Qing'. It's a reference to 뭉탱이/ 'mungtaengi' meme
\end{lstlisting}