\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (10)}

The expressions of the guards stiffened.

The Steel Nodus was the most advanced weapon in Zhongyuan.

It was a formidable crossbow capable of piercing steel plates with its immense power, and it could even fire five steel bolts with a single loading.

However, Makseok scoffed.

"Hmph, you wolves are finally showing your true colors. How dare you point your weapons at me, Makseok of the Seventh Banner, who serves the Emperor?"

"The Northern Army also serves the Emperor."

"Do you think that dogs guarding the yard dare to share a table with the servants? Aren't you just lowly beasts that can be replaced at any time?"

To think that a mere lieutenant, a replaceable and common wretch, would dare to be so impertinent.

You are just mere animals, and only the Embroidered Uniform Guard are servants worthy of serving the Emperor.

How dare you act against an official of the Embroidered Uniform Guard?

"I've never seen such a bookish weakling who hasn't even tasted the blood of those Yeojin barbarians. Do you think that's something a useless glutton who wastes food while the dogs guard the house should say? Is running away at the first sign of battle the way these gluttons repay our kindness?"

To think that there are so many useless bastards leeching off the national treasury while flirting with those nearby.

And you're saying that those who ran away without even seeing the completion of the operation are talking about servants?

Amidst the tense atmosphere, Qing thought.

Who said it?

That if you live as a slave, you will brag about your collar? Was it a collar? Chains? A leash?

A competition to see who is the more loyal dog of the Emperor?

However, Qing's attitude was not appropriate.

Culture is relative, and one should respect differences.

The spirit of China can be summed up in two lines.

Rise up, those who do not wish to be slaves!

We'll make sure nothing happens when you rise!

Thus, since only those who wished to be slaves remained in China, it was only natural for them to brag about how shiny their collars and chains were.

After all, the character 士, meaning scholar, originated from the image of a person with outstretched limbs, lying flat on the ground in a display of respect.

It was a posture known as prostration, where the entire front of the body was completely pressed against the ground, lying flat (a proper prostration should crack your forehead in one go). It was a posture of complete submission and abasement.

Incidentally, those Eastern barbarians mistakenly believe that prostration is similar to a deep bow or something.

Therefore, even the most noble among the lowly, the scholars, would lie on the ground more humbly than dogs.

So, bragging about one's collar was a natural part of being Chinese, a characteristic that went beyond mere habit.

However, Qing could not understand this.

That was why she felt a bit deflated.

So they were just going to fight with words after drawing their swords?

I guess dogs that bark don't bite.

But not fighting and just leaving was fine too.

After all, two precious packages were loaded onto the cart.

She needed to get them out safely before doing anything else.

If only I were in perfect health, I would have slaughtered them all, but I'm just a spring roll with a burst side, so I can't.

How depressing.

Qing chewed on her sweet potato with a sorrowful heart.

Anger is my strength! I will chew and swallow the world like a sweet potato! Oh, why is it so sweet?

Qing crunched on the sweet potato as if she was chewing on the world.

Makseok of the Seventh Banner, one of the Eight Banners of the Embroidered Uniform Guard, was trembling.

He was the one who started the war of words, but his own heart was being scratched, making him unable to contain his anger.

‘How dare he, how dare he……!'

It wasn't that Makseok was trembling because his spirit was weak.

To Makseok, the general was nothing but a lowly subordinate, a servant, and a lowly commoner.

After all, it was natural for one to be angrier when insulted by someone inferior.

In comparison, since the general was just a lieutenant, he had little impact from being insulted by the Embroidered Uniform Guard, who were technically his superiors.

After all, what did it matter if he was insulted by those who always insulted him?

Thus, Makseok's eyes gleamed, looking for any excuse, truly intending to draw blood.

And he continued to see Qing, who was still munching on her sweet potato.

"You, you wench!"

Makseok immediately recognized Qing.

Since she had the build of a bear, with a harness around her chest, and was facing away from the cart, it must be that bitch, he thought.

And then, firecrackers exploded in his mind.

"You, you bastards, treason, treason!"

"Watch your words. What treason? Do you think it's easy to frame innocent people as traitors just to advance your own career? It seems the rumors were not unfounded."

"Don't make me laugh! Didn't you use that wench to dare to draw a blade against the Embroidered Uniform Guard!"

Makseok pointed at Qing.

The general followed his finger, then sighed deeply and shook his head.

"What wench? Is there something wrong with your eyes? Where is there a wench here? You're just making things up now."

"Ahem. That's right."

Qing chimed in with a man's voice.

However, Qing's voice was also the best under the heavens.

Even when she tried to scratch her throat to produce a man's voice, it was originally so beautiful that it was a captivating, beautiful voice.

If one thought of it as a man's, they could pass it off as a man with an unusually effeminate voice.

But if there was even a hint of doubt, it was easy to notice that the voice was faked.

"Damn it, was she really a woman? No wonder the veil she was wearing looked like a woman's. So you were planning to sneak away by deceiving us from the start. Sir, we of the Thousand Households have nothing to do with this."

"Oops."

Wait, the atmosphere suddenly feels like I'm a common enemy.

Did this unscrupulous bastard just switch his words?

Qing slowly placed her hand on the harness around her chest.

"Hah, don't make me laugh! I saw that wench attaching your unit's banner to the carriage. Are you saying you would just hand over your unit's banner to a wench you have nothing to do with?"

"That's……."

"That wench dared to ambush the Embroidered Uniform Guard, harming six and seriously injuring two! And yet you still claim you are not traitors?"

"Let's speak properly, shall we? I was just calmly pulling the carriage when you suddenly attacked me. I thought you were bandits. And I definitely heard you say something like ‘Kill those fucking military bastards with the flag'?"

Qing tried to sow discord.

It was a fabricated story, but it surprisingly pierced the truth.

The general's expression crumpled.

"So you're saying you attacked immediately upon seeing the Dashing Sun Unit's banner? Sir? What is the meaning of this? Do those who serve the Emperor attack the Emperor's army without reason?"

"Hmph! Didn't I tell you I saw the fire reaching the firebreak and told you to retreat? Yet you dared to openly wave your banner and run away. Should I have just let you go?"

"Ugh."

The general groaned uncomfortably.

After all, it was true that they had disobeyed the order to die, so they had committed the crime of disobedience.

Seeing his great concern, Makseok's spirits soared.

However, as it was clear from Makseok's words and actions, they were just servants, while the Northern Army was nothing more than house-guarding dogs.

And servants never considered the possibility that a dog might bite them.

Thus, Makseok thought that since the general was agonizing over the situation, his spirit must have died down.

But the general's concerns were elsewhere.

If they attacked immediately upon seeing the banner, it meant that for some reason, the Censor hated the Dashing Sun Army like an enemy.

Even if it meant attacking the Emperor's most loyal servants, he had to survive.

While the general was seriously considering treason, Makseok was feeling very triumphant.

"Yes, you bastards, you're all very suspicious. Answer me this. Who exactly are you trying to smuggle in that carriage?"

"……I told you, it has nothing to do with the Dashing Sun."

"Oh? I'm sure there's a traitor in that carriage. Did you know that the traitor has gathered demonic adepts under his command to plot treason? That wench must be one of the demonic adepts the traitor has gathered."

Qing's eyebrows furrowed.

What's this crazy bastard saying? Demonic adepts?

Did that mean that a bastard who raised his realm with human blood was calling me a demonic adept?

"Are you saying you have nothing to do with them? Then prove your innocence by beheading that traitor yourself."

At that, the soldiers quickly moved to surround Qing, their spear points aimed at her.

Yeon Pa pushed Jayu into the carriage and threw a determined look at Qing.

It was a look that told her to leave her behind and escape with Jayu.

Qing sighed deeply.

Well, there's no other choice now.

And so, Qing sighed deeply and-

"How dare you. How dare you raise your heads so stiffly in front of me? How dare you keep your knees off the ground before the blood of the Son of Heaven?"

"Kuhahaha! You wench, you're finally showing your true colors! Are you thinking of using the Grand Prince's authority now? Give it up, your master is nothing but a traitor. Even so, if he's executed, his royal title might be revoked posthumously. Inform your master to obediently offer his neck."

After all, who would believe that she was invoking the authority of a Grand Prince when they had come to capture Grand Prince Deokhyun?

It was a fact that even Qing was aware of.

"You, you can't even recognize your master with those eyes of yours, so you should just pluck them out. I am Yeonsul, bestowed with the title of Princess, your master. The legitimate bloodline of the Imperial Family is right before your eyes, so how dare you keep your knees in the air?"

I am the princess of this nation!

Qing's stern shout flowed from her lips.

Yes, Qing's identity was none other than the legitimate bloodline of the Imperial Family, bestowed with the title of Princess, Princess Yeonsul!

Silence filled the area.

Caw, caw.

Coincidentally, a hungry crow of the winter season crossed the sky with a loud cry.

"……?"

The Embroidered Uniform Guards had expressions that seemed to question if they had heard correctly.

"……?"

The Northern Army also had expressions that seemed to ask, ‘What kind of bullshit is this?'.

"……!"

Jayu, crouching under the blanket, had an expression that seemed to realize something.

The horned colt! The big piglet-like kid! Why didn't I think of that sooner?

"……Haa."

Yeon Pa covered his face with his palm.

"Oho. What's wrong? I'm the princess, you know? I'm telling you there's a princess here, so why aren't you kneeling?"

The two leaders shook their heads.

"You wench, um, it seems that your demonic nature has reached your brain. Tsk tsk."

"To think you'd have such a strong constitution, yet your mind is so unstable. What a pity."

For some reason, they looked at her with pity.

Qing turned her head to look behind her.

After meeting the gaze of Yeon Pa, who seemed to be saying, ‘What kind of bullshit is this? To think you'd claim to be a princess', she felt a surge of anger.

What? What's with me?

So what if I said I'm a princess? Do I not look the part or something?

It was true that her attire was dirty and shabby, with a bulky, ill-fitting padded jacket that bulged to the right due to the unevenly distributed cotton.

And around her chest was a harness.

In one hand, she held a half-eaten sweet potato.

It was also true that she had been munching on it deliciously throughout the conversation.

Furthermore, everyone here had seen her skilled rickshaw-pulling and Herculean strength.

So when she suddenly claimed to be a princess…

Well, yeah. It was bullshit that not even a dog would believe.

Unaware of her own appearance, speech, and behavior, Qing's temper flared, and a vein throbbed on her forehead.

Qing reached into her money pouch and rummaged around inside.

It was hard to find, so she turned the pouch around and dumped its contents, finally finding what she was looking for and throwing it in a curve towards Makseok.

Startled, Makseok caught it and looked down at the object in his hand.

It was an intricately carved jade pendant.

The blood drained from Makseok's face.

A dragon and a peacock engraved in gold on the jade pendant.

The dragon had five fingers!

The peacock had nine tail feathers!

And the six-colored tassels of white, black, red, gold, and blue, with the addition of the noble purple, signified that this was a symbol that only one person in the world could use: the Empress, the mother of the nation.

Makseok's eyes blinked, he rubbed his eyes, and he even touched the pendant disrespectfully with his hand.

"This, why is this real……"

Because it was the Empress's genuine keepsake.

The very embodiment of a mother's concern for her daughter. 