\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (2)}

Even the greatest masters of the Unrestrained Realm were helpless in the face of a wildfire, so what could a mere, nameless soldier do?

Soldier Jin Shiho1 was utterly terrified, running with the sole thought of escape.

It was then.

Suddenly, on the right side of the road, a cart emerged from beyond a convex hill, soaring through the air.

A scene as if time had stopped!

The cart was suspended in mid-air.

A burly man, harnessed to the cart, had one foot extended forward, the other raised high with a bent knee, and both arms stretched back, holding onto the shafts for both cattle and horse.

He truly seemed ready to charge anywhere, even to turn back time itself.

However, everything that falls is in the sky.

Thump!! Screeeech!

The roughly landing cart drew a semicircle, its iron-rimmed wheels fiercely skidding and spitting sparks along the road.

It was an advanced technique known as drifting in the Western Regions.

The wheels scraping the ground, spitting sparks, rushed towards Jin Shiho.

Only then did Jin Shiho realize what this phenomenon was, this strange experience of time flowing hundreds of times slower, as if it had stopped.

This, fuck, this is a flashback-

Finally, bang!

With the impact that felt as if his lower body had been crushed, Jin Shiho soared like a kicked stone.

May you be cursed by heaven! Cursed by heaven!

Suddenly, he remembered a scene from the past, though he couldn't recall when exactly. Was it during his first raid? The image of an old man cursing in the pouring rain came to mind… Jin Shiho flew in a low arc, piercing through the bushes on the left side of the road.

Qing gritted her teeth, trying to control the cart that was sliding sideways due to inertia.

She dug her feet into the ground, but the cart continued to slide with a screech. Just as she thought she would have to use her left arm again, bracing for the pain, she felt a thud against the shafts!

The force pushing the cart sideways noticeably weakened. Without missing a beat, Qing used the technique of Heavenly Demon's Dash and succeeded in shifting straight.

What was that? Did I hit something?

Qing, inadvertently gaining a kill, cocked her head in confusion before thinking, ‘Well, it was probably just some bandit wannabe, so it doesn't really matter if I hit a few'.

"Move aside! Cart, no, rickshaw coming through! Ding-a-ling! Ding-a-ling! Get out of the way! Move or you might just die!"

Qing shouted in a rather gruff voice.

Of course, since she inherently possessed a clear and beautiful voice, even when roughened, it only sounded like a lovely, androgynous voice, considered low for a woman but high for a man.

However, contrary to her intention to clear the way, she instead attracted attention.

She was wearing thick layers of coats, making her upper body, especially around her chest, appear incredibly bulky. From the perspective of her homeworld, her height would be a hundred and seventy-six centimeters, making her look like a legendary barbarian chieftain.

Of course, for a barbarian who typically measured over six and a half feet tall, she would be considered a bit short. But still, her girth was impressive, wasn't it?

So, here was a person pulling a cart faster than a fit soldier could sprint, which was a strange sight, but considering the size of the person pulling, it was surprisingly convincing.

"Me too! Take me too!"

"Save me! Me too!" "Me too! Please!"

Requests for a ride poured in from all over.

A vein throbbed on Qing's forehead.

Do these motherfuckers think I'm some rickshaw puller?

Should I force-feed them hot soup up their noses to make them regret it, huh?

Hmm? Hold on.

If I carry a bunch of them, wouldn't I be able to escape naturally?

Come to think of it, it's not a bad strategy.

With a screech, Qing stopped the cart after sliding about three zhang.

She could have stopped it immediately, but if she did so, there was a risk of the cart flipping over.

After stopping, Qing raised her thumb and pointed behind her.

"Hey! Get on! First come, first served, six people! What are comrades for! If we're gonna live, we're gonna live together as comrades! Who would ever doubt a comrade!"

The latter part of her statement was incredibly unnatural.

It was an explanation for the Free and Yeon Pa, pretending to be soldiers in order to get away, so it was bound to be unnatural.

However, the soldiers were desperate.

With the fire chasing them and hearing the words ‘first come, first served', who would have the mental capacity to worry about the unnaturalness of her words?

"I trusted you!" "Thank you!" "I'm saved!" "Move, I'm first!"

The soldiers immediately rushed over.

Two, four, six. Eight. As soon as Qing confirmed the passengers, she kicked off the ground.

Due to the unexpected acceleration, one of them fell and rolled on the ground.

This was why seatbelts were important.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The soldiers who had set up their position on the eastern side of the mountain's foot were able to retreat quickly as soon as the flames erupted.

They ran eastward to escape, and when they looked up, they saw soldiers with long spears overlooking them from the top of the hill.

The escaping soldiers felt a sense of relief.

"Big trouble! Big trouble!" "It's a wildfire!"

"Haa, haa, phew."

As soon as the soldiers, who had run for their lives, crossed the line, they collapsed, fell to the ground, and made a scene.

Then, a general wearing a helmet with a fluttering red tassel sternly shouted.

"You fools! What kind of disgrace is this at the line! Can't you all get over the hill right now!"

"Y-Yes, sir……"

Even the exhausted and demoralized soldiers couldn't dare to defy a general's command.

So, with trembling legs, they managed to get up and reach the top of the hill. As soon as they crossed over, the scene on the other side came into view.

Naked corpses piled up together.

Beside them, soldiers with gleeful expressions were stripping the clothes off the bodies that were not yet undressed.

"What is this, ugh."

A soldier looked down.

He vomited a mouthful of blood, looking down at the spear tip that had pierced through his chest, through his very heart.

His legs, already trembling from the all-out sprint, gave out completely and he collapsed.

"Hey, the coat will get damaged. Hit the head. Smack the head! Are you going to clean up the blood?"

"But this has a better feel, you know? Besides, they're so soft. When I stabbed those barbarian bastards from Yeojin, they were tough and it felt like I was digging through muscle. Ptooey, what's the point of getting a salary if you're this weak?"

"That's just how these low-ranking soldiers are. But be careful not to damage the coats. Look at the quality. We can sell these after taking off the military supplies this winter."

"Wouldn't it be better to wear the supplies and sell these?"

As the fading conversation receded, the soldier realized the situation and thought.

‘How could they do this? Killing people and taking their belongings while laughing. They're worse than beasts. Unforgivable. They'll be cursed by the heavens. They should all go to hell!'

Then, he suddenly realized that it was the same thing he always heard when he raided villages.

Ah. I'm going to hell too. I should have lived a good life.

However, regretting only after disaster had struck was just regret, never repentance.

The general, looking down from about seventy percent up the hill, saw a very long procession of refugees appearing from the curved road below.

Half of them were equipped with armor over fur coats and carried huge steel crossbows on their backs, while the other half carried guandaos.

They were warriors of the Northern Army.

Like the elites of the north, they climbed the hill vigorously and saluted the general, despite their panting.

"Charge! I am Baekjang Sam Yeonjong of the Maenggwani Squad!"

"I see. What is the situation? What about the line?"

"General, the wildfire is upon us! The fire has crossed the southern firebreak! I have withdrawn everyone at my discretion!"

"Maenggwani Squad? I believe the Changyang Squad was supposed to be to the west of your position?"

"We withdrew immediately upon seeing the flames and joined forces with the warriors who were operating along the way. That is all!"

"Ahem. You did well for now. Help with the work in the rear and await orders."

"Charge!"

The general's expression hardened.

So the fire had finally spread. The Maenggwani Squad was responsible for the right side of the southern line.

It also meant that the fate of the warriors responsible for the left side was entirely unknown.

The bigger problem was that the fire was spreading towards them.

Wildfires spread faster uphill than downhill.

They were heading south of the N⁰amnyeong Mountain Range, but the wind was carrying it west, and this was the high ground to the west.

The general urgently kicked off the ground and ran.

"Commissioner, the fire has crossed the firebreak. It must have crossed the southern midpoint by now."

"What? How could the fire spread when the firebreak was set up like that? Hmph, what an incompetent fool. So? What of it?"

"We need to withdraw."

"Hmm. Withdraw. Withdraw. Withdraw….."

The chicken-faced man frowned deeply.

Then, a sly smile spread across his face.

"Alright. I will grant General Jang a great opportunity. It is a chance to carry out a glorious mission personally ordered by His Imperial Majesty. Along with one Baekho, defend the current line, and if any traitors try to escape, execute them and withdraw. Or you may observe and report when the blocked area becomes entirely uninhabitable."

It meant to guard the position until the fire was right in front of them, killing anyone who tried to escape.

However, when the wildfire was right in front of them, escaping would be a distant dream.

So, it was essentially an order to guard the line and die there.

But there was no right of refusal.

If he refused after hearing that it was a direct order from the Emperor, he would be branded a traitor on the spot.

"……Understood."

"Good. I will entrust this to you. Perhaps if you perform well in this military campaign, you might be posthumously promoted to Great General. A fine statue might be erected in your honor too."

Upon hearing the report, the adjutant burst in anger.

"Isn't that just telling everyone to die? How could he, those fucking bastards, those silk-clothed pieces of shit, those fucking retards who have never thrown a stone at a barbarian, how dare they."

"What do you mean die? They have to try and live. Pick thirty volunteers from the Daesun Squad."

"Do you think thirty will be willing to stay? If it were under the General's command, they would even jump into fire, but… well, it really is fire this time."

"Thirty. Prioritize those without wives and children. Soak their clothes thoroughly with water, send the steel crossbows and guandaos with the retreating troops, and arm them as lightly as possible. From this moment, the line will be moved to the top of the hill. The moment the wildfire is observed within a hundred paces, everyone will withdraw."

"Charge!"

Thus, the Northern Army was busy preparing for retreat, moving wooden fences and other obstacles to the top of the hill, when suddenly…

From the winding road below the hill, a huge rickshaw appeared.

Wait, a rickshaw?

The general rubbed his eyes.

However, even after looking again, it was indeed a rickshaw. A cart that should have been pulled by cattle or horses, loaded with soldiers and being pulled furiously up the hill by a large man.

"What is that?"

It was truly a display of strength worthy of Xiang Yu3 himself.

Are there still such warriors among those not from the Northern Army?

No, hold on, why was such a warrior mixed in with the other rejects?

Then again, not all rejects are incompetent.

Even if it was just to save a comrade, pulling a cart with the strength of a beast could be considered an act worthy of a true warrior.

Just like myself right now.

"Well, that… That's quite a sight to behold, isn't it?"

"Ha, what is that? Is that the strength of a human?"

Even amidst the hectic preparations for retreat, the Northern Army soldiers turned their heads one by one to witness the extraordinary scene.

"That warrior is too precious to be killed here. He is just the kind of valiant soldier my army needs."

"What should we do?"

"Have the flag ready, let him pass. He is too valuable a talent to be dealt with here."

Even as they climbed the steep hill, the speed of the rickshaw did not decrease.

Even amidst the chaos of preparing for retreat, the adjutant personally held a flag and prepared to welcome the warrior.

Qing was catching her breath, inhaling deeply. Inhale, Inhale, exhale, pant, pant, pant.

It had been over ten li, and even though it was a cart loaded with eight people, sprinting at full force was a bit much even for someone who had gone beyond the Transcendent Realm.

Every time she breathed, her sides screamed with stabbing pain.

But it was bearable.

In fact, from some point on, the stabbing pain felt strangely refreshing, like tearing off a scab that wasn't fully attached. What should I call this? A peculiar feeling.

However, the sweat was not welcome.

The skin under her thick clothes was soaked, her underwear was already damp, and the rising sweat was truly unpleasant, something she hadn't felt in a long time.

Her heart was pounding, her breath was coming in gasps, and when she tried to expand her lungs, her sides reminded her, ‘We're injured, don't forget!', poking her with reminders. On top of that, she was sweating buckets and her vision was getting blurry.

It was an utterly irritating situation!

So, of course, she was furious when someone suddenly blocked her path.

"Out of the way! If you don't move, I'll run you over!"

"Wait, halt!"

Qing slightly kicked off the ground and grabbed the shafts for cattle and horses, lifting her body.

But the wheels kept rolling and the cart continued forward.

However, as the back of the cart sank and the front lifted due to the principle of leverage, Qing, hanging parallel to the shafts like she was doing pull-ups, raised both her legs and extended them forward.

And thus, Qing's feet slammed into the chest of the one blocking the path.