\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (4)}

However, Yeon Pa immediately admired it.

When did she learn that and start using it?

This wench, she's a peerless genius who can immediately master any secret manual just by skimming through it. Ah, right, she even mastered the Ethereal Steps, so I guess it's not surprising.

It seems she truly is a peerless genius.

But the admiration was short-lived, as an imperial guard aiming for the wheels ran alongside, matching her shoulder to shoulder.

Killing intent exploded in Yeon Pa's eyes.

How dare they! The royal carriage where His Highness resides!

A royal carriage referred to a vehicle in which the king rode.

Although it was nothing more than a sturdy military cart for carrying goods, anything that carried a noble person inherently became a noble object!

Yeon Pa extended her thin sword.

It was a thin sword, with a blade only about the width of a finger, yet long.

It looked as if it would break immediately upon impact, but when combined with the Wheel-Turning Demonic Arts, it would transform into the most vicious sword under the heavens. No, it was a spinning blade of Sword Force, a vicious circular saw of the heavens.

The guard, who had raised his sword high, infused with Sword Force, had his heart torn apart by the circular saw that dug under his armpit, instantly severing his breath.

One might question how a Transcendent Realm martial artist could die so trivially, but what martial artist in the world had experience fighting a moving carriage while running?

In that sense, the Embroidered Uniform Guards were making history in martial arts, but as is often the case with humanity's new endeavors, the beginning was rather awkward.

The progression of martial arts was linear.

It was natural for martial arts to extend in the direction the body was moving, so it was an obvious principle that didn't need explanation.

But what about a carriage?

Attacking from behind did not inflict much damage, so to break the wheels or attack the driver, one had to match shoulders and extend their weapon to the side.

Moreover, the carriage was speeding downhill.

One couldn't even catch up without running their hardest.

Thus, to even attempt a strike, one had to sprint with all their might, using all their Qinggong just to keep up.

"Die!"

A guard shouted from Qing's left.

Qing took a step to the right, and the blade, infused with Sword Force, neatly sliced only the livestock.

Missed! If you miss, you get hit!

Deeng! The Buddha's Palm struck his thigh.

With his leg twisted, the guard landed headfirst, planting his face into the ground, sliding three yards while plowing with his face before his neck gave out and he landed on his back with a thud.

A guard who had jumped over him came close to Qing again.

But a thin sword suddenly appeared, piercing his shoulder.

With a crash, he spun roughly and fell.

It was Yeon Pa's spinning saw blade.

Simultaneously, a scream came from the right.

A pigeon-helmeted guard clung tightly to the carriage wheel, raising his sword high.

A shining blade, a sign of someone who could use Sword Force.

And so, he ignored the axes that were repeatedly striking his head and shoulders, and swung his right hand down-

Whoosh. The blade cut through the air.

As he was running with Qinggong, trying to simultaneously swing his right hand at the left carriage wheel resulted in an awkward angle.

What the hell? How can someone at least at the Transcendent Realm not manage this?

Are the Embroidered Uniform Guards all a bit off?

But the one Qing was riding with was the ultimate expert in being off.

So, what could she do? She had to evade.

Meanwhile, several guards, having distanced themselves to the left and right, ran ahead of the carriage.

Far ahead, they stopped abruptly and turned around. Qing leaped back and stood upright on the carriage's driver's seat.

The reins of a livestock were tied to their chest, and since the chest was right behind the head, whether it was a cow or a horse, the length had to be generous.

The draft animal had deviated from its shaft, now standing on the driver's seat.

Naturally, the front of the carriage tilted downward.

Thump! The carriage's front support scraped against the ground, making a harsh grinding sound.

Above it, Qing held the Moonlight Great Sword with both hands, raised it straight, bent one leg, twisted her waist (it hurt), pulled it back tightly, and then swung with all her might, unwinding her coiled body.

The attempt to block her from the front was good, but the result was a head flying up and over the bushes.

"Diiiie!"

To the left, another one had overtaken them.

Qing stomped her foot.

With that, the front of the carriage bounced up due to the recoil, and the sharply sliced left shaft of the livestock pierced through the guard's belly.

"Argh!"

The guard, impaled in the stomach by the shaft, was instantly pushed into the driver's seat, pressed against it.

"How dare you ride without paying! Death penalty!"

Qing's judgment fell upon the guard.

It was a harsh sentence for the crime.

But since Her Highness, Princess Yeonseul, was pulling the carriage, it might be considered a fitting punishment for daring to ride without permission.

As Qing was about to grab the reins again, her field of vision suddenly cleared.

The downhill road curved along the hill, revealing the opposite mountainside.

She couldn't be sure of the height, but it was a cliff, a sheer drop.

Until now, the straight path had been strange, as mountain roads were supposed to be winding.

And if the reins were released, the carriage could not be controlled.

"Ah shit, seriously!"

Qing leaped forward again, running in front of the carriage.

"You wench!"

Perhaps dissatisfied with the judgment, Gye Doo caught up and shouted.

It wasn't just a shout.

Thump! Thump!! Thump!!!

Three heavy stomps on the ground.

He flew through the air at a terrifying speed, shooting forward like a projectile, then suddenly seemed to kick off an invisible platform in the air, charging in a straight line.

Gye Doo's elbow was pulled back to his side and then thrust upward.

It was a pose that made one want to apologize for some reason, as Gye Doo flew like an arrow.

Suddenly, a burning dragon's form appeared, wrapping around his arm and extending into a palm strike.

What's that! Why is it so cool! It can't be a long spear of fire, can it? It must be a Blazing Dragon, Blazing Dragon, right!?

But Qing, too, had a white dragon sealed in her arm.

Hastily, she raised her left hand with the Moonlight Sword, and ice fragments scattered from her right shoulder as the white dragon of ice and snow coiled around her arm.

Qing thrust her palm forward without hesitation.

A battle between the Blazing Dragon and the Frost Dragon!

It was a truly epic showdown that could have come straight out of a legend!

With clenched teeth, Gye Doo's eyes were filled with determination to decide the battle with this one move.

Although Qing couldn't see it.

And at the moment of their clash-

Qing kicked the ground and evaded, flinging her body to the left.

Am I crazy? Why would I take that head-on?

There were many enemies, but Qing only had one life.

It was like a minion on the screen.

So even if the enemy died after causing a small scratch on her, it was still a loss for Qing.

It was a truth Qing had always kept in mind while enjoying her hobby in her homeland.

Gye Doo's all-out attack, with all his might, cut through the empty air.

It was because Qing had acted as if she would accept it, only to dodge at the last moment.

It could have been an epic showdown, but Qing didn't want to be more epic, as she already had an epic chest.

However, since the Frost Dragon had already been summoned, Qing's palm struck Gye Doo's back.

But because Gye Doo's speed was so fast, instead of hitting his back as intended, she ended up slapping his butt really hard!!

The human fireball, no, the human engulfed in flames, was it? I'll be the Fist of Blaze!?

With a bruised butt, Gye Doo fell, scraping along the ground and sliding under the carriage.

And then, the winding road was right ahead-

Qing urgently reached out, planted both feet on the ground, and lay back.

Thud, her back hit the driver's seat, and screech! Qing gritted her teeth and tried to slow down the carriage.

The soles of the stolen felt shoes seemed to be on fire, and in an instant, a sense of liberation came with a whoosh, as Qing's rough scream of "Aaaagh" erupted.

My soles!

However, according to the law that one doesn't scream when it really hurts, Qing screaming meant it was still bearable.

Human soles were originally tough, and Qing's, which had transcended human limits, were even tougher.

As the carriage slowed, the guards quickly closed in.

"The wheels!"

Yeon Pa shouted.

Simultaneously, blades flashed on both sides of the wheel axles.

Qing gritted her teeth and leaped up again, and the carriage, accelerating almost instantly, bounced a few times, ku-oong, kungkung, spitting sparks.

Then, another sharp turn!

Once again, sliding sideways and performing an amazing maneuver, Qing's expression hardened.

It was a steep hillside with a hellish winding road leading down in a 弓 shape.

I'm going crazy, seriously.

There was no way to go crazy, so she had to turn instead.

Qing grimaced and tightly gripped the intact shaft of the carriage.

Adding more speed here would make it impossible to handle the sharp turn.

Even for Qing, attempting a full-speed 180-degree turn would only result in the carriage being flung into the air.

"Grab it! Kill them!"

Angry shouts followed from behind.

With each step, the soles of her shoeless feet slapped against her insteps.

Every time she ran, her bare soles touched the road, causing a pain as if they were being torn apart, while simultaneously feeling like she was being whipped on the instep.

Qing gritted her teeth and made the first turn!

The carriage swerved, pulling the reins, and Qing, almost lying down, gritted her teeth.

Suddenly, a crack appeared in her ribs, causing her to gasp, and ahk.

Qing's eyes rolled upward.

The carriage, now behind the unconscious Qing, struck her.

The footrest of the driver's seat hit Qing's calves, and the angled part of the driver's seat slammed into her back.

"Argh!"

With a pain that felt like her spine was folding in half, Qing's eyes, which were mostly white, instantly returned to normal.

What the hell? I think I just lost consciousness.

Gasp, huff, gasp, I can't breathe.

With no regard for the carriage, Qing sat in the driver's seat, desperately trying to catch her breath.

Scrape, scrape, scrape, the front support of the carriage dragged along the road, then suddenly snapped and broke off.

Thump, the carriage dropped, and Qing, who was catching her breath, leaped out due to the recoil.

Tears welled up, blurring her vision, and through it, she saw figures blocking the way ahead.

The carriage had to follow the winding path of the road, but the Masters could simply jump down in a straight line.

Can I get through them?

And if I do?

Can I handle another turn on this winding road with this body?

Qing looked to the left, down the slope.

Then, she shouted loudly.

"Hold on tight! We're going down!"

Qing sharply changed direction in the middle of the slope.

There was no way to make it down the 弓-shaped road.

Then? 弔!

Now, it was really a straight line, a straight line!

As the carriage entered the steep slope, practically a cliff, Qing pulled the reins tightly, detaching them, and then leaped onto the carriage.

Only then did Yeon Pa, who had been looking ahead, became horrified.

"What are you doing?!"

"It's too late anyway! Freedom, where are you!"

"Here, here."

Qing wrapped her arm around a horizontal bar of the carriage, pulled Yeon Pa and Jayu close, and hugged them tightly.

The carriage seemed to shake as if it were falling apart.

It was an incredibly terrible ride.

The tremendous acceleration felt through the vibrations.

Thump! The impact of hitting the road, and now-

This must be what they call zero gravity.

Qing's body floated, hanging onto the horizontal bar.

Yeon Pa and Jayu were in the same situation.

A beautiful hand reached out, pulling the stunned soldier behind them, into the space between the floating carriage and the three people.

Immediately after, Kung!!!

Crash, the role of a cushion was perfectly executed by the soldier as all his ribs were instantly shattered.

"Argh!" "Ugh." "Guhk!"

Qing, Yeon Pa, and Jayu screamed.

Without even a moment to ask if they were okay, the carriage soared into the air again, lifting their bodies.

"Aaaaaaaah……!"

A soldier screamed as he was flung away, leaving a trail of his voice.

Flying, then thump! Flying again, then thump! And flying once more, then thump!

With Qing hugging the two of them, facing the sky, every time the carriage crashed, she had to bear the weight of two people.

If it hadn't been for the cushion, she would have passed out long ago.

In other words, it hurt just enough to not pass out.

Qing gritted her teeth so hard that if it weren't for her superhuman teeth, they would have all been shattered by now.

And then, finally, as the carriage flew once again-

----

The guards watched the carriage with dazed expressions.

To cut the road in a 弓 shape meant that it was originally a slope that people could not climb.

To run straight through it, no, usually one wouldn't describe such a sight as running.

They would call it falling, or consecutive falling.

So the guards stopped and watched the rare sight of a carriage flying.

If Gye Doo had been there, he would have immediately ordered them to chase after it, but since he had collided with the ground at full speed, he was still unconscious.

And after regaining consciousness, he was destined to realize that one of his buttocks had become significantly larger, resulting in an asymmetrical pair.

"That's… incredibly sturdy……"

Suddenly, a guard muttered.

At that, the other guards nodded in agreement.

If it had been the Northern Army's commander, he would have been proud.

Why make carriages out of expensive rosewood for no reason? someone should have shown this scene to the commander who said that.

If they made one and used it for decades, it would be much better, as the commander had said.

Thus, the incredibly sturdy carriage, after its final flight, was seen shattering into pieces.

It wasn't broken or cracked, but rather, the joints came apart, separating into materials.

That was because rosewood was ironwood, a wood that was harder than ordinary steel made by mediocre craftsmen.

So, the disassembled carriage, along with its scattered materials and passengers, flew into the air.

And then, they fell.

Only then did the Embroidered Uniform Guards realize their mistake.

Loud splashes erupted as a thick river caught the falling people.

It was the Musu River, flowing north from the northern foot of the Nymph Mountain Range. 