\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (8)}

Sometimes in life, there are moments when time seems to slow down, as if it would stop at any second. Moments when a single blink of an eye stretches out to feel like an eternity.

This could be in the face of a life-threatening crisis, or when someone or something more precious than life itself is in danger.

Or, when one falls in love.

For Ryu Mangyeok (a member of the Jinyiwei Special Forces, thirty-seven years old, married), who came to the granary hoping to find a pretty woman, such a moment of miracle had arrived.

As the woman who had been squatting down turned around, her smiling face, perhaps mistaking him for someone she knew, was imprinted in his eyes.

That moment stretched out like an eternity.

A true beauty is beautiful from any angle, and here was the most beautiful woman in the world, slowly turning around in an infinitely drawn-out moment.

Her large eyes, from which one could fall head over heels, and her long, delicate eyelashes fluttered towards him, blossoming like flower petals.

Ryu Mangyeok just stood there like a helpless child, merely staring without end.

It was an incredibly dramatic moment for him.

It wasn't for Qing.

What's up with this fucker?

She thought he was Jayu, but then some random guy showed up, gaping like an idiot with glazed-over eyes like some junkie, just staring at someone else's face.

She had been using a hat and scarf as a disguise when pulling the cart, but since she had swum in the river, her veil had gotten soaked, so she had come out bare-faced to dry it.

Qing knew she was pretty.

But she didn't know how harmful her beauty could be, especially to men, how it could shatter their eyes and brains with its powerful destructive force.

She just saw a spaced-out face and thought that he didn't look like a local resident.

It was impossible for a well-dressed guy in silk clothes to exist in such a rural village.

Especially if he was carrying a sword.

As Qing's expression turned fierce, Ryu Mangyeok snapped back to reality.

"Ahem, Young Lady. This humble warrior is not a bad person. Please do not glare at me so."

"Have you ever seen a bad person who admits they're a bad person? Ah, I guess a lot of them do, huh."

It was common for human scum to take pride in how bad they were.

Thanks to this, there were more than a few who boasted about their Evil Karma in front of Qing, only to end up suffering more painfully.

Of course, numbers don't lie.

Qing checked the three blurred digits above the warrior's head.

Given the density of the blurred digits, she could tell that it was at least a number, even if she couldn't tell what number it was.

But the first digit of this warrior was densely packed, so it was at least over 199 points.

"Well, anyway. Who are you?"

"This humble warrior is called Ryu Mangyeok of the Jeongjeongryuga. Have you, by chance, heard of the Jeongjeongryuga?"

"Is it a famous family?"

"Indeed. If I may boast, it is a prominent family of landowners in the Jeongjeong area, owning a manor of one hundred and four rooms. A famous family, among famous families in the capital, no less. And this humble warrior owns a seven-room manor in the capital."

What is this? Self-aggrandizement? It seemed like he was boasting about himself.

"And this humble warrior is an Imperial Army soldier, a member of the Jinyiwei Special Forces."

That was how Ryu Mangyeok introduced himself.

In fact, for someone of the Jinyiwei, self-introduction was practically a come-on.

Good family, owns a self-owned house in the capital, has a good job with a high monthly salary, and his work takes him outside often, so he's not home much.

Truly the best husband material!

But Qing's expression was sour.

So what do you want me to do about it?

And aren't the Jinyiwei those bastards who were chasing me like they wanted to kill me earlier?

Ryu Mangyeok saw Qing's expression and realized something was off.

It seemed this country woman didn't know how great these things were.

"The Jinyiwei are the greatest generals who serve only His Imperial Majesty's orders. And this humble warrior is a member of the most elite force among them, the Special Forces, where just breathing gets you promoted and the path ahead is solid."

Qing looked at Ryu Mangyeok.

Did this fucker come alone?

There were quite a few of them earlier, so where were the rest?

Could she escape in her current state?

That guy who spat fire from his hand seemed to be at the Unrestrained Realm. It might be one thing if it was one-on-one, but she was alone, while the enemies were in a group, and she was the only one with a handicap.

"You don't have to be so wary. I'll be honest. I fell in love with you at first sight, Young Lady. Will you be my wife?"

At that, Qing's eyes widened.

A sudden proposal on the first meeting?

And in a sweet potato storage in the countryside?

What is this? Is he insane?

Strictly speaking, he probably thought of Qing as insane.

Since she was a country girl, he probably assumed she would cry tears of joy and follow him if he offered to take her as his wife, not just a concubine.

Goosebumps rose on Qing's spine.

But regardless, this was a good opportunity to find out about the current situation.

Physical contact was more enjoyable for truth-seeking, but it took a long time, and the reliability of the information obtained wasn't particularly high either.

"Um, we've just met, how can you say such a thing to me so suddenly?"

"Ah! I haven't even asked for the Young Lady's name. I apologize. Would you do me the honor of hearing your esteemed name?"

At that, Qing smiled brightly and replied.

"This girl is Eon Yeonyoung of the Jinju Eon Clan."

By now, the name came out without any hesitation.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Selling out Eon Yeonyoung had little to no effect.

After all, even if Ryu Mangyeok, who had now gone to the afterlife, told the Grim Reaper that ‘Eon Yeonyoung killed me, that bitch is a bad person', the record would clearly state, ‘Died from shock due to pain from compound fractures and multiple organ damage after being thoroughly beaten by Ximen Qing'.

But one should always tread carefully, even when crossing a stone bridge.

It was definitely a growth on Qing's part to use a fake name even when dealing with a soon-to-be-dead person and to prepare for unforeseen dangers.

Even so, Ryu Mangyeok, who did not know he was facing the Killing Star of Heavenly Slaughter, tried to win her over by telling all sorts of stories he knew.

At least he probably had a clear conscience on his way to the afterlife.

Currently, the number of Jinyiwei stationed near the north gate was a total of twenty-four.

Two were severely injured and considered out of combat, but that still left twenty-three. Among them was one Master of the Unrestrained Realm, five Transcendent Realm Masters, and the remaining seventeen were Peak Realm Masters.

They had all received His Imperial Majesty's special grace, which, as Qing knew, meant they had received some sort of technique that involved sucking other people's blood and strengthening the body.

According to the warrior, it was called the Imperial Grace of Sacred Blood Great Technique.

It was said to be the greatest grace, with the actual blood of the Son of Heaven mixed in, and was given only to the highest-ranking and most skilled warriors.

The other warriors received the Imperial Grace of Conferred Blood Great Technique, which was a lesser version that still involved the blood of the Imperial Family.

It seemed that the warriors who received this technique were called the Special Forces.

So the blood of the Imperial Family is like some kind of elixir or something?

Then if I eat it, will I become stronger too?

But didn't that Poison Grandfather, the Grand Clan Lord of the Tang Clan, say it was originally an evil technique of the Blood Cult?

Since it involved collecting people's blood, it could be assumed that they mixed in a drop of blood and pretended it was some kind of imperial grace.

Just like how they twisted the names of stolen martial arts into Imperial Grace of something Divine Technique.

So, the warriors who ground people up to gain strong bodies and bonus rock-hard stamina, which made women go crazy, had their loyalty reach the sky.

Although, she didn't particularly want to know about the latter.

From the start, the fact that he boasted about it in front of a woman meant that this fucker was utterly irredeemable.

Somehow, it seemed like all the carts had long dicks. They were all bastards who deserved to die.

Regardless, the strength of the warriors was far from ordinary.

Of course, they were bastards who lost their speed as a side effect of the technique.

It was quite a serious side effect, considering that the initial thirty-one couldn't even keep up with a single cart.

Thanks to that, only Qing's complexion turned serious.

Whether there were side effects or not, a group of tough bastards coming in droves was not something to be taken lightly.

"Now that the Jinyiwei have arrived in the village… (crunch, crunch) I did manage to take one down, but we don't have much time, so (gulp) we should get out of here quickly. Ah, how can sweet potatoes be so sweet even when raw? Is it a honey sweet potato?"

Qing spoke with a serious expression while munching on raw sweet potatoes.

They didn't have time to cook the sweet potatoes, so raw ones had to do.

The content was serious, but since the speaker was munching on sweet potatoes, it didn't quite land.

Yeon Pa thought.

Well, it's to, um, replenish her stamina, right?

She's probably stuffing sweet potatoes into her mouth to save time, so she can help His Highness escape…….

This is not it.

Just a while ago, she had cooked a whole iron pot full of porridge and devoured more than half of it, and now she was munching on sweet potatoes again.

Yeon Pa, who had been trying to give her points somehow, gave up this time.

There had to be at least a little bit of water left in the glass to positively evaluate that there was still water, but when it was completely dry, it was impossible to see it in a good light, no matter how hard one tried.

"So, what do you plan to do?"

"I'm just going to sneak out. They said they're near the north gate, so we'll go around the foot of the mountain to the west."

It was a simple plan to sneak out to the south while the Jinyiwei were resting.

"Luckily, I brought a handcart with me."

At that, Jayu and Yeon Pa's faces turned pale.

Again? Another cart?

Seeing this, Qing smiled.

"Don't worry, I'll make sure the ride is comfortable this time. We can put a mattress on it and cover it with a blanket."

At that, Yeon Pa snapped out of it.

Was this the time to complain about a cart?

"No, why would you, in your condition, pull a cart again? And with a mattress on it?"

"It'll be better for Yeon Pa to recover, and Jayu will be much more comfortable that way, won't he?"

Yeon Pa's eyes became moist.

That damn recovery excuse!

How could a woman, born as a woman, willingly pull a cart like a horse or a cow?

In a way, it wouldn't be strange for her to be furious, grind her teeth, and vow revenge, being treated like a mare or a cow.

Yet, she volunteered herself.

Even though her own condition was far from perfect.

How could such a person exist, with such a beautiful and lovely heart?

A hundred points were added to the baby's admirable thoughtfulness.

Qing's back, as white as jade, was still vivid in Jayu's mind whenever he closed his eyes.

It was probably something that would never fade for the rest of his life, the most beautiful back he had ever seen.

But at the same time, the horrific wound on her side, swollen as large as a pumpkin, was also etched in his memory.

Even so, there was no other way.

He had already lost several of his men, whom he considered family, and he didn't want to lose Yeon Pa as well.

It was a moment of utter helplessness that was bone-deep.

A deep shadow fell over Jayu's expression.

"Um. Friend, I'm sorry. Yeon Pa's condition isn't good, so I can't refuse."

"Hey, what are friends for?"

"A friend, huh……."

"Now then, let's pack up. I'll go modify the cart a bit. This time, I'll have to reinforce it here and there. It probably won't be as sturdy as a military cart……."

Modifying the cart wasn't too difficult.

Because Qing's strength was the greatest under heaven, a monstrous woman whose strength could make even Xiang Yu rename himself to Namcheong.

Moreover, with the skill of a novice carpenter, modifying a handcart didn't even require any special tools.

Thus, Cart No. 2, with its improved ride comfort, was born.

"This is, um, unexpected."

"A young lady with remarkable handiwork. Well, having various skills is always a good thing."

Ten points were added for the baby's handiwork.

Anyway, the lumps seemed satisfied.

However, whether it was due to the curse of Cart No. 1, which suffered all sorts of hardships before being utterly destroyed and dismantled,

Or because she found modifying it fun and put too much effort into it, as it was often the case that when something was thoroughly prepared, it ended up not being used.

There was no opportunity for Cart No. 2 to show its worth.

As soon as they sneaked out the south gate, they ran into a heavily armed military force. 