\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (7)}

"General, 100 members of the Daesun Expeditionary Force have all gathered. The rest have begun to withdraw."

At his adjutant's report, the general frowned.

"100? Didn't I say 30?"

"Everyone wanted to stay, so we couldn't help it. We can't have comrades fighting each other, can we?"

"Hah, these foolish bastards."

"It's not like they're going to their deaths. How could we dissuade them from their sincere intention to serve the general and be a little late in returning?"

Going to their deaths.

At those words, the general's expression hardened.

After all, who could survive in such a wildfire, and why should they risk their lives to watch over it?

Especially when it involved the lives of a hundred of his precious subordinates.

"It's not a place to die. Yes, if they were swept away by the wildfire while just watching it spread in a place like this, what a dog's death that would be. The Northern Army, which protects the North, dying in vain would truly be a disservice."

An imperial order was to be carried out as is.

If one tried to interpret the Emperor's orders, at some point, loyalty would turn into convenience and be used for one's own benefit.

Therefore, even if the Emperor's order was to jump into a pit of fire, a suicide order, it had to be carried out as is.

So, what this general was saying now was precisely an act of defying such an imperial order.

"What about those Embroidered Uniform Guard bastards?"

"They were the first to flee."

"When the last withdrawal group leaves, we will also depart after one gak1. The order was to watch until the fire comes, so wouldn't that be enough to say we watched until it came?"

"That is absolutely right. Then, it would be pointless to wet our clothes, wouldn't it? It would only hinder us."

"Right. Also, make sure to be properly armed. We might encounter bandits on the way back."

"Bandits, bandits, you say. Understood. Allegiance!"

If it was discovered that they had withdrawn much earlier than planned, they would silence those who knew.

The adjutant, immediately understanding, saluted with perfect discipline.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The guards, wearing only their undergarments, warmed themselves by drinking tea.

Makseok seemed to dislike this sight, as he smashed the wall with a bang! He then disappeared, turning around the wall of the next house.

The guards thought it was better this way and frowned.

They had even closed the door to keep out the cold air, but he had punched a hole in the wall, and then, because he disliked that, he turned to enter through the door.

Truly, he's a petty bastard whose mind is narrower than a grain of rice, they thought.

It could be seen as childish and petty for a man of his age to act that way.

But for men, as they age, their emotional sensitivity increases, leading to childish behavior. This is a sad truth about men.

In Qing's hometown, it wasn't difficult to observe middle-aged men, also known as department heads, acting childishly. They would sulk for various reasons, not closing doors properly, or turning off air conditioners, claiming to save electricity when they never cared about it before.

One of them picked up the debris from the broken wall and started a large fire.

It was then.

"Anyone want to go for a walk around? Who knows? Maybe there are some village girls left behind. If we're lucky, we might have some fun."

"What? Why? It's a hassle."

"That bastard is at it again. Is your dick hard again?"

"You guys don't get it. It's in these rural areas that you might find a peerless beauty, you know? A village girl who doesn't even know she's beautiful."

At this, the adjutant clicked his tongue and said.

"A village girl looks like a village girl. They look like either a cow, a chicken, or a pig. And they didn't even put out the fire before running away. Do you think they wouldn't take their women with them?"

"Well, what if they left some treasure behind? They might not know what's valuable and just left it there."

"Even villagers have eyes, and if they find treasure, they'll take it all and run to the city, eager to stop being villagers and become city folk. In these isolated villages, you won't find anything worth taking except maybe a handful of grain, even if you turn the place upside down."

"But you never know, do you?"

"Well, if you insist, I won't stop you. If you find any dried tea leaves, bring some back. He's the boss, so we should at least give him a cup of tea. Just don't bring back dried shepherd's purse and call it tea leaves like last time. If you're going to bring shepherd's purse, bring some fish sauce and rice too."

A burst of laughter erupted.

"But it tasted pretty good, didn't it? You ate all the leaves too. I'll look for some since you seem hungry."

The one who had stood up spoke with a sly grin.

"So, anyone else going treasure hunting?"

"Good luck. If you find a woman, don't keep her to yourself."

"The Embroidered Uniform Guard's loyalty is truly dead. Just watch, I'll bring back a peerless beauty as my seventh concubine."

And so, the frivolous Embroidered Uniform Guard, still wearing his damp golden winter uniform, walked out the door.

No one imagined that it would be his last appearance.

This was the limitation of the primitive and uncivilized ancient China.

If the entertainment culture of Zhongyuan had revolutionarily developed and the art of cinema had been invented earlier, the man would not have dared to venture out alone.

Originally, the first victim targeted by a murderer was always a woman who went to wash first. And if there were no women, it was decided to be the most frivolous one.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Old people with children approaching marriageable age cannot help but unconsciously evaluate the opposite sex around their children's age.

The more lenient elders, upon seeing a decent person, would think, ‘It would be nice if our son/daughter-in-law was like that,' or ‘They would be a good match with our so-and-so.' Conversely, upon seeing a bad person, they would think, ‘I hope they don't bring home such a terrible person,' and then laugh it off, thinking, ‘I'm being silly.'

However, the more meddlesome and childish elders, who have not aged gracefully, would meticulously assign scores to each individual, acting quite outrageously.

In truth, Yeon Pa did not think highly of Qing.

It was understandable. Putting aside her decent appearance and her baby-bearing hips, there was nothing else that met her standards.

Of course, those features alone were promising, and she imagined how lovely the Grand Prince's offspring would be, and how if they were abundant, the royal household itself would be paradise without needing to seek the heavens.

Qing received a plus five points for her face and figure.

However, while her appearance was outstanding, it demanded corresponding conduct. Yet, this wench was not particular about men, and her interactions were far too casual and rough.

And what about that watermelon-sized chest?

It was common knowledge that women with large breasts were inherently lewd, vulgar, evil, and even stupid.

Of course, she knew that Qing was not like that, but how would the world know?

It was a significant flaw that would make the whole world point fingers and say, ‘How could you take such a vixen as your main wife?'

Qing received a minus ten points for her face and figure.

Still, if the Prince was fond of her, so be it. She thought she would have to give her a good talking to and instill some discipline.

But one positive aspect was her sense of loyalty.

She had seen how Qing had stood up for her friend at the Tang Clan, so she figured a woman who valued friendship so highly would cherish her husband even more.

Qing received a plus five points for loyalty.

Thus, adding and subtracting, she came to zero points.

Actually, it wasn't even zero points.

Her speech was rough, her demeanor like that of a general, she didn't show respect to the Prince, and her lack of education was evident from just a few words.

So, the score plummeted further down.

But now, there was a massive addition to the loyalty score. To put a number on it, it would be 100 out of 10, or 10,000 out of 100.

What kind of person in this world would dedicate themselves to saving a friend without regard for their own rotting body?

From what Yeon Pa could see, Qing's side was already severely infected and rotting.

If Qing had known, she would have asked, ‘Eh? Me?'

Moreover, this foolish and silly girl didn't even show any signs of pain, acting cheerfully instead.

Wasn't this consideration to avoid causing worry?

Now that she thought about it, if she were to find a partner, there was no woman in the world as good as her.

She would keep her loyalty for a thousand years, and the fact that they had met again in a dangerous time and saved each other's lives was surely a sign of a bond sent from the heavens.

One cannot go against the will of the heavens.

So Qing received 1,000 points, no, wait.

How dare a lowly old servant like me score our precious new baby, no, the future mistress of the royal household?

If Qing had known, she would have said that Yeon Pa was not just drinking a cup of kimchi juice2, but guzzling a whole jar of broth in one go.

"I'll go check the grain storage. It's that time of year, so there might be a lot of sweet potatoes. Wow, roasted sweet potatoes, that's crazy, that's insane. I'll be back soon."

Why roasted sweet potatoes were considered crazy was unknown.

Well, if a baby says it's crazy, then it's crazy. But…

"Stay here. I will go."

Yeon Pa stopped Qing.

"No, you should rest. Your wounds have all reopened, so you should circulate your Qi a bit more."

"We are both in poor condition. It is better for this old woman's body, which will be discarded anyway, to suffer."

"……It's a strategic decision. A Master needs to conserve strength for when danger comes, doesn't she?"

"……You speak as if you're all grown up, but you're just a stubborn mule, stubborn as an ox. Being a woman with such a strong will… Hmm, then again, it's better than being a spineless yes-woman."

Minus five, but plus ten!

It was practically a situation of ‘There's still half a glass of water left, huh?'

"My friend should rest. It seems our Prince is quite thoughtful. Look, doesn't the Prince say he will personally come for the baby? Even though your body is in such a state, you still move around. But, Your Highness, do you even know what a sweet potato looks like? It's a dull, purple, elongated, and plump crop."

"Sweet potatoes are purple? Not yellow?"

Jayoo felt a great sense of dissonance.

It was because Yeon Pa was actually encouraging this.

But the shock about the truth of sweet potatoes was greater.

Purple?

How could such an auspicious color exist in a common crop?

Do they turn yellow when cooked?

At that, Qing shook her head.

What an ignorant young master, not knowing the ways of the world.

How could I possibly send him alone?

"Jayoo, you should rest. I'm grateful for your concern, but honestly, you'd probably lose a fight even against a stray dog in your current condition."

Yeon Pa's expression turned grim.

How dare she speak so disrespectfully to a prince! What kind of manners are those!

But if someone was speaking the truth without hiding anything, wasn't that a blessing in itself?

After all, a bitter medicine is good for health!

Yeon Pa's expression softened again.

"Ahem, even a stray dog would be too much for His Highness, but…"

"What, you're looking down on stray dogs? A healthy adult should run away when encountering a stray dog. If you get bitten, you might get rabies and die. There's no cure for rabies. Even the Guangdong medical sect can't fix rabies, you know?"

"Stray dogs are that dangerous?"

"Of course."

"I see. I didn't know."

"You must be tired, so get some more rest. I'm a Master, and Yeon Pa is a Supreme Master, but you're not, so…"

"……I understand."

Honestly, the two of them didn't need to look for sweet potatoes in the warehouse, as there was a large sweet potato bulging prominently at Qing's side.

It was the color and shape of a sweet potato, just the size of a pumpkin.

However, Qing had already thought of roasted sweet potatoes.

So, regardless of whether her side was torn or not, she needed to at least get a whiff of sweet potatoes.

Now it's December, so wouldn't there be plenty of sweet potatoes left in the warehouse, harvested in November?

Even if people were fleeing, they would prioritize grains over sweet potatoes, so there must be at least some left, she thought.

But do they have tinfoil in Zhongyuan?

If I just throw them in the fire, they'll be burnt, not roasted.

Is there no alternative?

Should I try steaming them with less water, like how they steam chestnuts, and then shake them vigorously?

Qing was happily imagining as she drooled, heading towards the grain warehouse.

And so, with a heart full of anticipation, although it was a bit too full since she was seriously expecting a lot, she still excitedly flung open the grain warehouse.

Because of that, her side, which had been torn open, screamed in protest, causing her to shudder and go ‘Ughhh'. But then…

So, sweet potatoes, do we have them?

We do!

Qing's expression brightened.

To think that she would deduce the presence of sweet potatoes based on the season and actually find them.

She was now a seasoned martial artist, fully worn and experienced!

Such advanced martial artists can even steal sweet potatoes from someone else's warehouse.

Who am I? The Thief God. Who is the Thief God? Ximen Qing.

The Thief God's great achievement worthy of such a title: Sweet Potato Heist!

If Cheonyu Hak, who was preparing for the spring semester in Taiyuan, had known, he would have been utterly infuriated, perhaps even collapsing from the stress.

As Qing was grabbing a sack of sweet potatoes and also looking around for other things…

What's this? Is it a taro? Is this a taro? It doesn't look like a taro, though. It's too small to be a taro, right? Is it some kind of yam? Let's see.

Uwegh, euheub, ptooey, ptooey, ptui! It's bitter, it's so bitter!

Sheesh, why would they put a Heavenly Demon in the grain storage?

It's confusing since it's not even edible.

Qing shuddered at the terribly bitter, unpleasantly sour, astringently tingling, and spicy taste of the Heavenly Demon, like ginger.

According to the Huangdi Neijing, it was said to contain all the terrible tastes of the world. It was considered the least palatable medicinal herb under the heavens.

While Qing was making a fuss, spitting and feeling nauseous after tasting the Heavenly Demon…

Step, step, the sound of leisurely footsteps approached.

What, that Jayoo guy, I told him to rest, but did he follow me to help?

With that thought, Qing turned around. 
