\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (3)}

The adjutant flew through the sky.

Whether it was an incredible coincidence, or a fateful encounter arranged by the heavens, the adjutant, who had successfully flown through the air against his will, landed right in front of the general with a thud.

"Oof!"

"Hmm. Are you alright?"

The general held the adjutant up.

At this, the adjutant exhaled a breath he had been holding in.

"Huuff, yes. I am fine. Hm? Why am I fine?"

"You sound like you're not fine. It might have looked rough, but I pushed rather than kicked you since I didn't intend to harm you at all. So, of course you're fine."

After all, although the sound was loud, he had used the reaction of his knee to push rather than kick.

Since he had shown mercy with his kick due to the two red marks and the two-digit Evil Karma, the adjutant had survived. But he couldn't know the reason behind such an action.

However, he could still tell that he had been intentionally spared.

"It seems the flag has been taken as well."

"Ugh. If only they had just accepted it nicely."

Even if he was pushed, the impact of flying through the air and hitting the ground was enough to make his body ache all over.

"If you had come into my camp, I would have nagged you then. Well, I suppose if they were carrying an injured person, they might be in a hurry."

"Then, it would be difficult to nag them……"

Meanwhile, Qing stomped on the ground again and resumed her sprint, holding a flagpole in her hand.

What was this thing that kept flapping about?

Since her harness was fastened over her chest, her hands were not particularly restricted when climbing the uphill road.

Qing looked at the unfamiliar pattern on the flag. It looked like a military flag. I wonder if holding this will stop them from attacking me?

Qing tucked the flagpole into the back of her collar.

Thanks to this, the cool air entered through the back of her neck, providing a refreshing relief to her sweaty back as she ran.

And the end of the hill was just ahead.

I wonder if it'll be okay once I get over this.

Qing did not slow down, so the cart passed the crest of the hill.

Her field of vision expanded and just like a carriage that had hit a speed bump at high speed, the cart was flung into the air.

Thump! The cart landed on the road.

The cart then rode down the steep slope of the downhill road.

The direction of travel, which had been pointing towards the sky, suddenly plunged towards the ground below, rolling down the hill.

"Uwaaaah!" "We're falling! We're falling!"

The passengers screamed as they experienced the cutting-edge thrill ride at least 500 years ahead of its time.

One of them even jumped out, unable to overcome his fear, and rolled on the ground. It seemed the people of Zhongyuan were still too uncivilized to enjoy the amusement culture of the future.

The Northern Army soldiers, who had been preparing to withdraw from the camp below the hill, saw the handcart speeding down the slope like mad.

However, behind the driver of the handcart stood a flagpole.

The flag, fluttering wide as if it would rip apart, was the famous Great Shun Army, the banner of the Great Shun's Lieutenant General.

Since there was hardly a unit in the Northern Army that had not received help from the Great Shun's camp, they all respectfully made way.

Of course, their respect was only to this extent.

They just moved their bodies out of the way, thinking that getting hit by that thing would probably separate their bones and flesh.

Qing sped through them.

Thus, after racing down the downhill road and through the military camps spread out on both sides of the road, she suddenly slipped through an open gap in the palisade.

And then, she entered a deserted mountain path.

She had escaped from the soldiers.

Only then did Qing slowly start to reduce her speed, so as to not pull on the cart.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Led by a man wearing a helmet with a chicken's head, a group of Embroidered Uniform Guards in silk clothes marched in rows along the road.

Each of them wore a helmet on their heads, and the front of each helmet was adorned with a bird's head ornament, with a long neck extending forward.

These gaudy bird-head helmets, which would have made Qing grimace in disgust, were actually the most coveted items among all martial artists of Zhongyuan.

This was because they were items that could only be worn by high-ranking officials.

Among them, the most prized bird-head was the chicken head.

In Zhongyuan, a chicken head was, surprisingly, a very auspicious symbol, representing, in order of importance, scholarship, wealth, valor, and good fortune.

Therefore, the chicken-head helmet was a symbol of immense power, something that could not be dreamed of unless one was at least a general of the Imperial Guard.

The only helmet higher than this was the phoenix helmet, worn by the Emperor when he went on campaigns, so commoners could not dare to even dream of it.

Thus, the chicken-head helmet was also the most glorious helmet an individual could wear.

If Qing had known, she would have been horrified by such tastelessness.

No, she didn't even need to know.

It was horrifying just to look at.

So, Qing was horrified.

Countless bird heads stretched their necks out, looking at her.

What the hell? Is this the standard of fashion in Zhongyuan?

Don't they feel ashamed to wear such a tacky helmet?

As the guards withdrew to both sides of the road, the handcart, making a loud clattering noise, drew all their attention, so each and every bird-head on their helmets was inevitably directed towards the handcart.

The guards were also puzzled.

What's that? A handcart? Is it a falling handcart?

Since the mountain range descended to the east, the mountain path was a continuous downhill.

A handcart was running down at a tremendous speed.

The chicken-head grimaced.

He had ordered that every single ‘bandit' who dared to burn the mountains of the heavens and exploit the common people should be killed.

But there was a bandit, pulling a handcart with other bandits, boldly speeding down the middle of the road. And what was that flag?

The chicken-head, upon seeing the flag of the Great Shun's camp, ground his teeth.

Wasn't that the flag of the bastard he hated the most?

Then, a sudden thought occurred to him.

Could it be that this guy was pretending to be one of them to escape on his own?

Why did you leave him in a death trap if you were going to let him escape like this?

A vivid hatred was born in the eyes of the chicken-head.

From the perspective of the general, this could be considered unfair.

It was too great a hatred for just having defied him a couple of times, a hatred that went beyond mere dislike.

However, this was the nature of humans.

No words were needed for a human to hate another human.

It was human nature to hate someone for no reason, just because they were unpleasant to the eye, and to hate someone who was doing well even more than one's parents' enemies.

Compared to the future civilized world of Qing's homeland, the chicken-head was rather innocent.

At least he hated someone for a reason, did he not?

Even if one knew nothing of the other person's face, name, personality, or occupation, if a single, meaningless phrase rubbed them the wrong way, future civilized people would shower all sorts of curses and pray for them to die in the most painful way possible.

At any rate, the chicken-head blocked the road and roared with his Inner Qi.

"Halt!"

Qing's mind raced.

The most tasteless helmet-wearing bastard told her to stop, and his expression was vicious, showing no intention of hiding his intention to not let her go.

His Evil Karma had three digits.

And on both sides, those wearing bird-head helmets also had three digits. From their gait and footwork, it was obvious they were well-trained in martial arts.

Then what?

They're all people I should kill. No, for now, I have to get Free safely away.

"I don't want to!"

"Wh-What?!"

"If you don't want to die, get out of the way! Chicken-head!"

Qing drew her Moonlight Sword (No. 10, Extra Large) and pointed it forward.

It was a posture reminiscent of a Western knight's lance charge!

"You wench!"

At that, the chicken-head crossed his arms and brought them forward.

It was an attitude of trying to block the lance charge with his body, which could also be said to be as bold as the madness of an old man with paranoid delusions who tried to confront a giant windmill in the manner of Western knights.

However, the chicken-head had something he believed in, as in that instant, a fiery Sword Force surged, turning his forearms crimson.

In that moment, Qing gripped the handle of her Moonlight Sword with both hands and pulled it back behind her shoulder.

The fire of her soul, which had been ignited and turned, rotated, and the sunset-colored Sword Force drew a half-moon.

A horizontal slash aimed at the waist, pretending to thrust.

As the chicken-head hurriedly lowered his forearms,

Crash!

With a heavy sound of Sword Force colliding, the chicken-head, bent sideways like a sickle, was pushed away by the tremendous force and fell.

However, Qing also exhaled sharply, going ‘Huuk'.

Originally, when a sword was swung to slash, there was no impact if it cut through, but if it was blocked, a portion of the force exerted would return to the user.

In academic terms used only by a very small number of the most intelligent people in the world, it was also referred to as ‘reaction force'. This was a concept so difficult that ordinary people could not even dare to understand.

Although it wasn't a complete reaction force since the chicken-head had been knocked away, it was enough to cause intense pain as if her strained side was about to burst.

Damn it, why isn't it healing?!

If her side had been listening, it would have found it absurd and wanted to burst from the injustice.

It takes time for things to heal, you know.

"Commander!"

A guard flew over and caught the chicken-head.

Even after that, the chicken-head slid back for quite a while before checking his sore forearm, only to find it deeply gashed and bleeding.

It's nothing much when it's someone else's blood, but one's own blood is as precious as gold.

The chicken-head's eyes widened.

"How dare you! Kill them! They are rebels!"

The guards simultaneously sprang forward.

They rushed towards the speeding cart, using their Qinggong.

Qing's Qinggong was unparalleled in the world; no one could dare to follow, they had said.

But that was not the case when she had a cart full of people behind her.

The leading guard jumped high, casting a shadow over the cart.

Instantly, a spear infused with True Qi struck the guard's abdomen.

The guard, hit in mid-air, fell powerlessly, rolling dozens of times before tripping his comrade and causing them to fall together.

"There's a Master on the cart!"

"Stop it first! Aim for the wheels, the wheels!"

"What are you doing! You bastards! Protect the wheels!"

Yeon Pa shouted hysterically.

At this, the nameless soldiers sitting on either side waved their bandit weapons, threatening the guards aiming for the wheels.

But how long could mere soldiers last against trained martial artists?

Even if one side was blocked by Yeon Pa, what about the other side?

Qing became desperate.

Since Free was inside, if the cart was destroyed, it was all over.

Since it was a downhill, the cart would go down on its own even if she didn't pull it, so for now, she should unfasten the harness.

Qing hurriedly grabbed the harness around her chest.

However, it was a harness that had been increasingly tightened by the force of pulling a heavy cart.

It was already so tightly fastened that it dug painfully into her armpits.

As Qing struggled with all her might, the harness wouldn't budge, blocked by her large chest below and her shoulder bones above.

Just as Qing was about to use force to break it…

"You wench!"

The chicken-head, having caught up, extended his left arm, stretching out a hand glowing with Sword Force.

In response, Qing had no choice but to counter by extending her sword.

In that instant, the chicken-head's eyes lit up, and he grasped Qing's sword.

What the fuck? You're grabbing it?

Qing's eyes narrowed.

The fire of her soul flared in her pupils.

Kiiiiiiing!! Sparks flew from the chicken-head's grip as the sound of metal grinding rang out.

As his hand stung, the chicken-head was startled and shook off his hand.

In that gap, the Moonlight Sword drew an angry trajectory and struck the chicken-head's shoulder with a thwack!

Damn, this fucker's tough.

She couldn't properly imbue her sword with strength while running at full speed.

Even so, to think that striking with a sword covered in Sword Force would result in a thwack instead of a slash or a cut.

The chicken-head, whose shoulder was hit by the force of Xiang Yu's strength, staggered, tripped over his own feet, and tumbled to the ground.

However, as expected of a Master, he quickly got up and narrowed the distance, shouting.

"Heaven-Shattering Demonic Arts! Cursed demonic human!"

"Who's calling who a demonic human! You're the one using Fire Demon Arts!"

Qing shouted back without yielding.

If a hand was turning red with Sword Force that looked like flames, then it had to be the Fire Demon Arts. It couldn't be anything else.

At that, the chicken-head yelled back.

"It's not Fire Demon Arts! It's the Imperial Grace's Fire God's Palm!"

"Is that another fake imperial knockoff?! I'm not using the HeavenShattering Demonic Arts, but the Space Hero's Divine Technique! Who's the one using Demonic Arts now?!"

The chicken-head's forehead bulged with veins.

Fake imperial, he says?! How dare he utter such blasphemy!

And what the hell is this Divine Technique?

How can a divine being be attached to the front of a technique?!

Yeon Pa, listening to their exchange, also had a vein popping out on his forehead.

I gave this wicked woman a Secret Manual for nothing! 