\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (12)}

Mak Seok urgently stretched out his palm.

Clang! The tip of the sword and the palm collided, producing a loud bang.

Heh. I'm not some nobody in the Peak Realm who struggled against a fake Unrestrained Realm anymore.

I have now evolved into a Transcendent beyond the Transcendent Realm, a Transcendent-Transcendent.

The immense Inner Qi of Qing turned into Sword Qi, leaking out and boring into Mak Seok's palm.

Mak Seok was pushed back five steps, spewing blood.

Qing had her own accumulated frustrations.

"Do you! Have a problem! With me! Being a princess! What's it! To you!"

Each word was imbued with emotion, as powerful sword strikes flew.

The Sword Qi continuously drew semicircles, and Mak Seok was busy warding off the strikes by conjuring fire dragons, though they were more like fire-worms due to lack of time.

The sword strikes, seemingly straightforward, would suddenly curve midway to slash at an arm, or abruptly change direction. Nevertheless, each strike was powerful.

The trajectories of the sword, if dissected one by one, resembled the Moonlight Sword of the military, but they would change mid-way, twisting and turning at right angles in a manner so foolish it could only be followed by children imitating martial artists.

However, the strikes were strangely powerful, and since the next move was utterly unpredictable, he was hard-pressed just to block the oncoming Sword Qi.

Then, suddenly, the Sword Qi split into three!

Mak Seok gritted his teeth, flames erupting and wrapping around his shoulder-

Thud.

Suddenly, a rough push from behind made Mak Seok stagger.

It was the Northern Frontier Army.

They had fearlessly rushed in to aid in the battle between Supreme Masters, thrusting their spears.

However, even the soldiers were taken aback after their thrust.

Five spears with sharply honed blades had simultaneously stabbed from behind, but it felt like hitting a cliff; their hands felt like they were tearing apart, and they had only managed to push him one step forward rather than inflict any damage.

But in a battle between Masters, even a moment's hesitation could be fatal.

Didn't Qing herself almost end up with three breasts after blinking just once?

And Mak Seok had stumbled mid-motion.

Three crescent moons drawn by Qing's Moonlight Sword overlapped diagonally and swept through, slicing his side open and cutting off fingers that fell to the frozen ground with a thud.

"Argh! How dare you!"

Mak Seok's eyes rolled back, and suddenly, he was covered in blue Sword Qi, flowing upwards like the clear light of the sky.

It was a scene that would have made the Kunlun Sect go mad with envy, but how could the Daoists of Kunlun, living far away in a foreign land, see this?

As he channeled the Sword Qi upwards, Mak Seok's body slowly began to rise.

Just as Qing lowered her body in caution…

Black objects flew in and covered Mak Seok.

It was a dark, murky net.

And not just one, but another net was thrown over Mak Seok, followed by more nets spreading like a spiderweb from all directions, wrapping around him tightly like weighted pendulums.

Covered by five layers of nets, Mak Seok struggled with his Divine Arts, but fell from a height of three fathoms, landing embarrassingly on his buttocks.

"Nice!"

Wow, nets!

When Qing was on the receiving end, she found no other tactic as annoying as this.

But now that it was used against an enemy, she realized there was no weapon as wondrous as this.

Qing grinned and repeatedly stabbed with her sword.

It was a truly despicable expression.

"Wait, argh, you're being cheap, fair and squa-, argh."

"What, cheap? Who was it that ganged up while pulling a carriage!"

Each time Mak Seok swung his arm, the sound of ripping nets was loud.

But he was covered in five layers.

No matter how many nets he tore, some part of his body was always caught.

When he reached out, his side was stabbed, when he stepped back, the net caught his feet, and when he turned his waist, his hair was pulled as if grabbed, making him sway left and right.

Mak Seok's eyes filled with rage.

Ah. I know that feeling.

Qing pulled back her sword in understanding.

Then, with a powerful thrust, the sword pierced Mak Seok's lower right chest, between the chest and abdominal muscles.

Qing's eyes lit up as she felt the sensation of soft insides being torn apart by the rotating Sword Qi. With a bright smile, she roughly pulled out her sword.

"Cough."

Mak Seok coughed up blood.

He then crouched on the floor, continuously spewing chunks of internal organs mixed with blood.

With his internal organs shredded by the ferocious rotating Sword Qi of the Round Heaven Demonic Sword, he was practically a living corpse, just barely breathing.

Qing swung her sword once to scatter the blood and gore, then sheathed the Moonlight Sword with some difficulty.

Although the sword was long and heavy, making it difficult to show off in a cool way.

Mak Seok died, entangled in nets, with dozens of spear points aimed at him.

Since only a few knew that a master of the Unrestrained Realm was imperfect, the vigilance did not cease even after Mak Seok's death. Only after a long while did the General approach, flip the corpse with his foot, and rummage through his belongings.

Thus, holding up a jade token, the General pretended to wipe it with his sleeve, examining it closely.

Five claws on the dragon, nine on the peacock's tail.

It was a symbol that only the companion of the Son of Heaven could possess, recognizable to anyone with common sense.

As he carefully rubbed the beautiful gold engraving, a technique so exquisite it was hard to fathom, the General's mind raced.

What kind of conspiracy had he become entangled in?

Was the Emperor trying to secretly kill his own brother, and did the Empress send the Princess to interfere and save the Prince?

But the General was known for his competence in the Northern Frontier Army, as well as being the leader of the Great Circulation Unit.

This was proof of his ambition.

Those without ambition did not rise in name, even if they were competent, and those with only ambition could not rise in name without competence.

A time when unusual power struggles were occurring in the Imperial Palace was the moment ambitious people had been waiting for.

An opportunity to spread one's wings and soar!

The General knelt and respectfully presented the jade token.

"This lowly one of the Northern Frontier Army greets the Princess. Will you forgive this foolish one for not recognizing your noble visage?"

"I was hiding my identity, so I have no intention of blaming you. Therefore, the General is blameless. I will vouch for that."

Qing readily forgave him.

She was simple-minded, but also inherently direct.

She didn't particularly mind being addressed informally.

And she hadn't really been treated poorly either.

"Thank you for your grace, Your Highness."

"Thank you for your grace!"

The soldiers of the Northern Frontier Army echoed in unison, bowing deeply.

The General glanced at the carriage.

It was obvious that Prince Deokhyun was inside, and his choice not to reveal himself meant that he simply wanted to stay hidden.

So, what should be done now?

The General carefully broached the subject.

"If I may ask, where does the esteemed Highness intend to go now? We would be honored to escort you."

"No need. I am heading south, and you are currently leaving the northern defense unattended, are you not? You should fulfill your military duties."

South meant Gwangseo or Guangdong.

And in Gwangseo Province was the Prince Suhyi's residence.

The General understood the true meaning of the operation.

A meeting of the Princes was something the Emperor disliked the most.

If three or four Princes, each commanding the military forces of an entire province, were to unite, just how many soldiers would that be?

It was practically an open declaration of their intent to rebel.

Thus, Prince Deokhyun had no choice but to move in secret.

If he were to travel officially, it would become a meeting of Princes, no different from revealing his rebellious intentions.

But by moving secretly, the Emperor could also make his move.

Didn't the Embroidered Uniform Guard say they would take care of the funeral arrangements when they tried to disguise an assassination as a bandit attack?

They were saying that although he was a traitor, they would maintain his royal status even in death, secretly killing him and conducting a state funeral.

A suspicious meeting of Princes.

The Emperor, trying to prevent it.

And the Empress, supporting the Prince?

This was a chance to become a meritorious retainer in a new era, a chance to change the very owner of the Dragon Throne.

The General's imagination ran wild, writing his own novel all by himself.

Still, since he was competent, the overall framework wasn't too far off.

After all, the Empress had only given the jade token to her daughter so she wouldn't be looked down upon wherever she went.

She was preparing to drive out the fake fortune-tellers and the strange witches from India in the Western Palace, but that was about it.

Regardless, the General's eyes were resolute.

"Your Highness, although this lowly one is lacking."

Then, he took out a token from his bosom and respectfully presented it.

"I will gather the hearts of the North and wait. Whenever Your Highness requires it, I will not hesitate to sacrifice myself."

Qing usually did not refuse gifts.

She just accepted it because it was being offered.

And honestly, as the number of tokens she collected grew, she found it increasingly fun.

But as Qing accepted the token, the General's heart pounded and tingled as if struck by lightning.

When a general handed over his identification, it meant he was pledging his loyalty, saying he had no problem being involved in whatever might happen later, so she could use him as she pleased.

"Well then, we will clear the battlefield and then return. Until we meet again, please take care of yourself."

They were saying they would clean up the bodies of the Embroidered Uniform Guards and destroy the evidence before leaving.

Qing agreed, and not wanting to get involved any further, she pulled the carriage and quickly left.

Since they didn't want to be seen with their poor eyesight, she just took the token. Qing squinted at the general's token as she pulled it close to her face.

On the front, it read ‘Northern Frontier Army, Great Circulation, Jang'.

On the back, there were three characters presumed to be a name. Combining the front and back, it read:

Northern Frontier Army, Great Circulation Unit's General, Yi Jaseong.

Qing tilted her head.

But why did he give this to me?

Does it mean to visit him in the North?

Why? Do friends not often give each other something, telling them to come visit?

Of course, he had given it to Her Imperial Majesty, the Empress, not to Qing.

After all, to the General, Qing was no different from the Empress, both being in the same boat.

But Qing didn't know that.

Because she was Qing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since the Embroidered Uniform Guards were all dead, there was no reason to avoid going north.

So, if they headed north, they could reach the city of Sunyeonghyeon in just half a day.

As they were pulling the carriage, Jayu, who had been unusually quiet, carefully opened his mouth.

"Um. Friend. No, um. So, um, yes, a Princess? Sorcery? Sohal?"

It was only now that he realized.

The girl he knew from childhood was still the same, but her status wasn't.

In fact, even when she was a child, that ten-year-old girl had a height similar to the seventeen-year-old prince at the time.

Well, I guess… When I first saw her in Sichuan, her demeanor and voice seemed familiar, and I found myself speaking comfortably without realizing it.

But then, why?

Why would she hide her identity and call her uncle her friend?

At this, Qing scratched her cheek and replied.

"Hmm. Honestly, I don't know."

"You don't know?"

"I don't know. I don't have any memories. In Zhongyuan, my first memory is waking up in a cave about five years ago? Wow, has it already been five years? Time flies. Anyway, I met the Empress on her visit to Shaolin Temple this summer, and she told me that the princess in the palace was a fake and that I was the real one."

"Cough."

"Did you know the Princess Yeonseul? She's a bit shorter than me, though. Did the Embroidered Uniform Guard not say that I was prettier earlier?"

"Honestly, after hearing that, I think you two are very much alike. But, you have no memories? I heard you were very ill."

"I don't know. I said I have no memories, right? So, do you think I look like a princess?"

"Honestly, you look exactly like a wild, untamed pony."

At this, Jayu's lips curled into a playful smile.

"Well then, niece."

"Ugh, what's with ‘niece'? I'm Ximen Qing, okay? Not Princess Yeonseul. I just pretended earlier because it seemed like a tough situation with enemies on all sides."

"Still, the bloodline doesn't just go anywhere. Niece. What kind of manners are these for your uncle?"

Yeon Pa's complexion hardened.

What was this conversation?

This ill-mannered tomboy was the real princess?

If she really was?

If Ximen Qing's true identity was that of a princess?

Yeon Pa's eyes filled with delight.

Wasn't this the absolute best-case scenario?! 