\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (9)}

The skilled soldiers of the Grand Circulation Unit shared glances and then began to move their fingers.

It was sign language, of all things. They exchanged glances, stretched and folded their fingers, and tapped their palms with their fists, conversing silently.

Just the level of sign language used to conceal their presence showed how elite this unit was.

These were the conversations exchanged through sign language.

-Halt. Civilian obstacles ahead. Two guard posts, one breach point, no sentries.

-Halt, keep steel crossbows' strings taut, have the vanguard approach and observe their movements.

-Civilian obstacle status closed. No sentries. No sign of enemies. Shall we breach?

-Hold judgment. Wait and listen for a while.

After a period of silence, about one quarter of an hour later…

The scouts, who had stuck close to the left and right sides of the closed wooden gate, sent another sign.

-No sign of enemies.

-Wait.

Thus, the General and his adjutant began to make their field assessment in hushed whispers.

‘They must have seen the wildfire and fled, don't you think?'

‘There are multiple plumes of smoke rising.'

‘They might have left without managing the fire properly.'

‘Even so, the smoke from afar is quite rough. It's not at the level of a blaze, so someone must have added new firewood to raise the fire.'

‘What shall we do? Shall we force a breakthrough?'

‘It's a civilian village. It's not a good time to cause unnecessary trouble, so let's first shout to draw them out, and if there's no response, we'll break through.'

‘Understood.'

Thus, the adjutant raised both hands high and approached the village's wooden gate, step by step.

He had been told there was no enemy caution, and indeed, he did not feel any other presence.

The adjutant took a deep breath and unleashed the powerful voice of a northern man.

"I a-!!" / Creeeaaak!

At the same time, the sound of wood twisting could be heard as the gate cautiously opened.

The adjutant blinked.

What? I haven't even said to open it yet, much less started introducing myself.

Qing was also startled.

What the hell? Why is this guy just standing quietly in front of the gate and then suddenly shouting when it opens?

Since the Embroidered Uniform Guards were resting at the northern side of the village, she was taking the opportunity to sneak out through the southern gate.

Just as the door opened, some guy shouted at the top of his lungs.

Thus, an awkward exchange of glances followed between Qing, who had a harness around her chest and a cart set up behind her, holding a sweet potato in one hand, and the stranger.

Crunch. Qing took a bite of the sweet potato in her mouth, Crunch, took a step back, Crunch, another step back, Crunch, three steps, Crunch, four steps. Her butt finally touched the cart.

Qing pushed the cart back with her butt, then slowly closed the door again.

Creeeaaak.

The sound of wood twisting as the gate slowly closed, as if to pretend nothing had happened.

The adjutant urgently shouted.

"Stop! Stop or I'll shoot!"

Gulp.

Qing swallowed the less-chewed sweet potato in surprise.

Fortunately, it was raw sweet potato, so it didn't choke her.

The threat to shoot didn't particularly impress her.

The fortified village's gate was made of thick planks, so even if a steel crossbow bolt pierced through, it would just be a spent force that had lost most of its momentum.

However, if there was a commotion, the Embroidered Uniform Guards would swarm in and it would be a disaster.

And if she was surrounded on both sides, well…

For now, Qing decided to stop as she was told.

In truth, such a gate was only sturdy when dealing with commoners; against a true martial artist, it was a flimsy obstacle that wouldn't even buy a few steps' worth of time.

Then, she thought of pretending to be a refugee woman.

She would say that she was escaping with her ailing old mother and an immature, sick younger brother.

It was questionable to leave through the southern mountain where a fire was raging instead of the intact northern gate, but any plan devised on the spot was bound to be as shallow as a puddle.

Thus, Qing cleared her throat and-

"Oh, right. If it isn't you. The rickshaw puller who was dragging that cart."

From the other side, someone pretended to recognize her.

It was a man in a thick blue coat. Since there were no women in the military, he must be a man, right?

Qing couldn't see clearly because her focus was wavering, but she could see small, acorn-like steel studs neatly arranged on the outside of the coat, shining silver.

It looked like a thick coat, but each of those round nail heads had a steel plate attached to its underside, making it a type of armor lined on the inside.

"Ah, now that I think about it! You! You're the bastard who dared to kick me!"

At that, the adjutant also recalled the rickshaw puller upon seeing Qing's build.

What great winter clothes could commoners possibly wear?

They were just clothes stuffed with cheap cotton to make them look puffy, and even then, the cotton wasn't evenly distributed, making some parts thick and others thin. Honestly, they were shoddy garments.

On top of that, she couldn't fasten a belt over the already fastened area, so it was a figure of a bloated giant wearing an ill-fitting veil.

The adjutant fumed, but somehow he didn't seem particularly hostile.

Qing coughed and imitated a man's voice.

"I-I apologize. But if you say I kicked you, I would be a bit upset. I merely pushed you slightly with my foot, thinking you might get hurt."

"What? Pushed with your foot!? If you push twice, you'll kill someone!"

"The flames were chasing us from behind, so I was flustered and couldn't see clearly. Uh, I apologize, but I don't have anything else to offer. Would you like a sweet potato, perhaps…?"

"What the, is this guy trying to mess wi-"

"Fine. If you're in a hurry, it can happen."

The General cut off the adjutant's words and nodded.

The adjutant immediately voiced his complaint.

"General! But this guy kicked me right in the chest! How can you so casually dismiss my efforts when I have served you with such loyalty!"

"That is something for you two to resolve. So, you, what is your name?"

Qing hesitated for a moment before answering.

"Uh, this lowly one is, um, called Eon Yeongyeong."

"Eon Yeongyeong?"

"Eon. Yeon. Yeong."

"Eo Nyeonyeong? Is your surname Eo or Eon?"

"It's Eon. Eo Nyeo Yeong. No, Eon Nyeongyeong. No, Eon Eoyeong. Ah shit, even I'm getting confused."

It was an incredibly difficult name to pronounce.

"Whatever the name. So, do you have any interest in military service? I saw your strength, and you seem like the perfect talent for my army. Would you like to come with me?"

"I appreciate the offer, but-"

Suddenly, the General raised his hand.

Then, with a series of deliberate sounds, cha, cha, chak, the soldiers, who had spread out in a semicircle, aimed their steel crossbows at her. Or at least, it seemed like they were aiming.

"It seems you misunderstood my words. I was not exactly asking for your opinion. Who in the world would want to serve in the Northern Army? They would rather die instead. Which do you prefer? Is it better to live and serve, or would you rather die?"

Join the army with me, or die.

Re-enlist with me, or die.

It was a truly difficult problem.

This was why a certain Western king, when faced with re-enlistment, had muttered, ‘To be or not to be, that is the question.'

Because living as a soldier was not really living.

To live inhumanely.

Or to die as a human.

This was the famous dilemma between re-enlisting or dying, between a wretched life and a peaceful death.

To be or not to be, that is the question.

To do or not to do, that is the question.

Surprisingly, Qing was a veteran of the military service.

Isn't it better to die than to go back to the army?

Even if the military is better these days, this place was even more ancient than that, an uncivilized world of primitive antiquity. It would be more shitty if anything, not less.

However, according to the law of the land, women could not serve in the military.

If you asked why such a law was established, it was because there were many who broke it. Or more precisely, there were many who made them break it.

In this era, military service was allocated by household, so if one didn't want to go themselves or send their precious son, the remaining option was their daughters, who were usually married off to other families anyway.

When a daughter was married off, the husband's family had to send a betrothal gift to the bride's family, an amount called the bride-price.

So daughters were raised well and then sold off for a good price.

Thus, if they gave up the bride-price, they could instead have their daughters cross-dress and serve in the military.

At any rate, Qing thought.

Since women can't serve in the military…

I can just say yes for now and hang around until I can get Jayoo and Yeon Pa to safety. And then, I can just say, ‘Oops! I was actually a woman!' and leave.

"W-Well, General. I have a sick old mother and a frail, ill child. I was on my way to take my mother to her sister's in Seonnyeong. If it's alright, may I take care of my mother first and then join you?"

"Ah, I see. No wonder you were pulling a rickshaw. So you weren't a soldier, after all? I thought it was quite a lot of strength for an unknown soldier. It seems you were taking care of your sick old mother."

The General nodded in understanding.

The adjutant, who had been displeased, also softened his gaze and showed a slightly warmer light.

Even if this guy had kicked an officer as high-ranking as an adjutant, if he was in a hurry to save his old mother, it wasn't something that couldn't be overlooked, he thought.

"Yes, it's a relief that you have another child. Even if you serve in the military, there will be someone left to take care of her. Seonnyeong, you said? Sam, you have the map, right?"

"If it's Seonnyeong, it's to the west along the foot of the mountain."

"Then we can stop by Seonnyeong and return to Beijing. Alright, everyone form up. We're still under the influence of the wildfire, so let's move quickly to get out of here."

"Ah, excuse me. General?"

At that, Qing called out to the General.

"What is it?"

"Well, there are some suspicious guys holed up in the village. I definitely heard them mention something about the Embroidered Uniform Guards."

At that, the General's expression hardened.

In contrast, Qing's expression brightened a bit.

Ah, so they don't get along?

"It would be no good to run into them. Hmm, you must know this area well, right? You must know a way to get to Sunyeong, or wherever it was, without being seen. Don't you?"

"I guess I do."

If it's about not being seen, wouldn't it be best to just break through the wilds and go west?

So it wasn't exactly a lie.

"Alright, then you lead the way."

Just as Qing was about to lead the way, pulling the cart…

"Halt!"

Even though the Embroidered Uniform Guards were notorious for their lax discipline, they had several Transcendent Realm Masters and a Unrestrained Realm Master as their leader.

So, how could they not have heard the loud voice of the adjutant coming from the south gate?

Of course, they all came out, albeit reluctantly.

It was because their grumpy leader had been annoyed that they were just lazing around even after hearing suspicious noises, complaining that they were neglecting their duties.

However, sometimes such grumpiness could yield results, as the Embroidered Uniform Guards managed to spot the figures of the Northern Army's Grand Circulation Unit, which should have been burnt to a crisp by now.

Thus, the Embroidered Uniform Guard's special detachment appeared at the wide-open south gate, arrogantly standing shoulder to shoulder.

Outside the south gate, the Northern Army soldiers had formed a surrounding formation.

"Well, well, if it isn't General Lee. I believe I conveyed His Imperial Majesty's august command to you, did I not? That you were to return after confirming that the traitors had been burned to death, all the way to the firebreak?"

"The wind was strong, so the fire spread much faster than expected. We have completed our mission as planned, so do not worry."

The tension was palpable, so Qing, who had immediately entered spectator mode, munched on her sweet potato. Crunch, crunch.

"Is that something you can really sa-"

"What is there that cannot be said?"

"Considering the circumstances, it does not make sense! It has barely been half an hour since we entered the village! But if you are already here, then-"

"Did Your Excellency see with your own eyes? I clearly saw with my own eyes that everything had burned down to the firebreak and withdrew, but if someone who was leisurely relaxing and enjoying himself in this remote area says otherwise."

"Y-You, what, what did you say? Relaxing and enjoying myself? How dare you speak to an elder with such disresp-"

"There are clear ranks, so there is no reason why I, a General, should have to use honorifics with you, an Imperial Censor. Show some respect to the military."

After cutting off his words three times in a row, Makseok's face turned bright red.

"Fine, you bastard! It seems you truly wish to die. Today is your funeral day. Everyone, draw your swords!"

Clang. The Embroidered Uniform Guards drew their swords.

The General also raised his arm, and the soldiers, who had already formed a semicircular encirclement, aimed their steel crossbows at the guards.

Qing's eyes sparkled. Her mouth didn't rest, munching away. Crunch, crunch.

Oooh, are they going to fight? Are they fighting amongst themselves? 