\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (11)}

Amidst the silence following Qing's thunderous declaration.

Makseok's seemingly muttered words, "But, is that for real?", echoed like a thunderclap.

"Greetings to Your Highness!"

The Northern Frontier Army immediately crumbled, their knees hitting the ground with a loud thud! as they planted their elbows on the ground.

They still couldn't quite believe it.

That the nation's princess had the physique of a burly man and was munching on raw sweet potatoes.

But it was an Imperial Censor of the Embroidered Uniform Guard, and a member of the Seven Cavalry at that, who had said it.

Moreover, his words were filled with an abundance of doubt, so there was no room for further suspicion.

It was the moment when the fantasy of a princess, something any man should have, shattered into pieces.

It was an inexplicable fantasy of a peerless beauty who was more beautiful, nobler, frail, and delicate than any other, like a single flower, a petal that needed to be protected with all their loyalty.

Perhaps that was why.

The Northern Frontier Army, with their foreheads pressed against the cold floor, felt a surge of tears.

Give me back my princess, my princess…….

Maybe it was because the floor was too hard and cold.

Their hearts also seemed to freeze, leaving them feeling cold and miserable…….

Yeon Pa was startled.

How did she even get involved with the Empress!

There was no way Qing was a princess.

After all, if that were so, no matter how long she had been away from the palace, there was no way the wise and intelligent Prince wouldn't have recognized her.

The Embroidered Uniform Guards were in a state of great confusion.

Some Embroidered Uniform Guardsmen knelt and raised their arms, but when they noticed that their commander was still standing, they realized something must be different.

The guardsmen, who had been kneeling with their arms raised, pretended that was what they had meant to do, stretching towards the sky, stretching their waists a few times, and then standing up again, appealing that they had been acting completely natural.

They didn't look very natural, though.

Qing frowned deeply.

"How dare you keep your knees off the ground?"

"Although it is indeed the Empress's insignia, there is no way that the princess would be here. If I am wrong, I will take my own life as an apology. May I have the honor of seeing your true face?"

Makseok answered respectfully for now.

But it was just respectful words. His words meant that he couldn't believe it, so she should take off the veil covering her face.

In other words, that bastard knows the face of Princess Yeonseul.

Qing wondered what to do, but decided to trust in the Empress Dowager for now.

Unless the Empress Dowager had gone mad from the grief of losing her daughter, she must have assumed that my face truly was the face of Princess Yeonseul.

With that, Qing removed her veil.

The beauty that most people who saw it did not hesitate to call the most beautiful in the world was revealed to all under the sky.

Makseok's eyes widened as if they would pop out.

Even in Qing's blurry vision, where a dozen or so figures jumbled together, she could still tell.

Then, Qing became curious as well.

So, there really is someone in the Imperial Palace who looks exactly like me?

However.

"Ahem, you almost fooled me. You wench, I mean, um, but, uh, are you perhaps serving the Empress Dowager? Are you a stand-in for the princess or something?"

Makseok asked hesitantly with a somewhat awkward attitude that was neither polite nor impolite.

"What impudent talk is that?"

"You clearly resemble Princess Yeonseul. However, Princess Yeonseul is not to such an extent…."

A spark ignited in Qing's eyes.

There weren't many in the world who could stand against Qing when it came to picking a verbal fight.

"Ah, yes. So Princess Yeonseul is not this beautiful? Is she ugly? You have truly lost your mind. How dare you belittle the Imperial Family? Do you think you can evaluate the precious bloodline?"

"No, that's not what I meant. The last time I saw her jade countenance, ahem, well, there were traces of pockmarks on her face."

"Oh really? So the Yeonseul you know is an ugly, pockmarked woman! And I'm a fake because I'm a beauty?"

Qing had learned some new information.

It seems I don't look exactly like her.

Come to think of it, the Empress Dowager did say that she recognized me with a mother's insight.

And even that Embroidered Uniform Guard said I resemble her.

"Wh-What are you doing, interfering with the matters of the Western Palace? Handling Prince Deokhyun is clearly what His Imperial Majesty comman…"

"Shut up!"

Qing shouted sternly.

"Now it seems you have truly lost your mind. What did you just say? Are you truly saying that His Imperial Majesty directly ordered the removal of his own flesh and blood? You will have to take responsibility for those words."

Makseok's heart sank.

Of course, it wasn't an order that had come down through the proper chain of command.

Of course, since ancient times during the era of the Yin and Zhou Dynasties, it was common for the emperors of Zhongyuan to treat their own brothers like this.

When it was possible, they had to be killed. To them, they were no different from enemies who could not live under the same sun.

However, the current Emperor, their father, couldn't bear to see his children kill each other.

As a result, emperors who were eager to slaughter their own brothers attached all sorts of restrictions to their children, telling them not to act like that and to get along.

In this situation, if a prince was openly killed, even if the officials all rose up together and demanded it, the one sitting on the throne couldn't be held accountable.

"No, that, those who know, will know."

Makseok was feeling wronged.

He was just following orders!

"Know what? Are you saying His Imperial Majesty ordered the massacre of his own army disguised as bandits and the slaughter of his own people, and even ordered to set fire to the mountains to cause a wildfire? Is that truly what you are claiming?"

"Ugh."

Makseok's words were stuck in his throat.

That was because it was the truth.

Qing, who had said those words, was also dumbfounded.

So the Emperor is really a son of a bitch, huh?

I said it, but it really doesn't make any sense.

How can someone like that become an emperor?

Qing, who had suddenly become enraged, turned her gaze to the kneeling Northern Frontier Army.

Even though she couldn't see their eyes clearly, she could still see that they didn't have a triple-digit count of Evil Karma. (Though there were some who did.)

Most had two-digit Evil Karma, some had one, and a few even had blue numbers.

"I grant the Northern Frontier Army the honor of seeing my countenance. Raise your heads and look at me."

At that, the Northern Frontier Army carefully raised their heads.

And then-

Gasp.

The burly rickshaw puller who had been munching on a sweet potato was nowhere to be seen. Instead, a heavenly maiden, as if descended from the heavens, was standing there.

Originally, clothes are completed by the face.

Even a lumpy padded jacket could not overpower Qing's beauty. Instead of a burly giant with monstrous strength, a peerless beauty with a refined appearance was standing there.

She had only removed her veil, but while they had been thinking, ‘No, our princess can't be like this!', they now thought, ‘Ooh, she's totally a princess. She's indeed a princess. She's so beautiful.'

Moreover, they were the Northern Frontier Army.

They were soldiers stationed at the forefront, where there were hardly any women, warriors guarding the borders in harsh, freezing lands. As such, their standards for women were severely low.

They were hungry beasts who would drool at the sight of an ordinary woman on the streets, so when they saw a candidate for the most beautiful woman of all time, their emotions were beyond words.

They were utterly dazed, wondering if this was a dream or reality. They looked and looked again, marveling at the sight, wishing they could watch forever until their death…….

"I ask the general there. Here stands an unparalleled traitor clad in silk, tarnishing His Imperial Majesty's name."

Qing didn't have much to go on.

If she gave them time to think, it would only make things difficult for Qing.

She couldn't just say, ‘Do you have any other proof? Let's all go to the Empress Dowager together and ask if I'm really her daughter or not, shall we?'.

"Will you just stand and watch?"

The general snapped out of his daze.

His judgment wasn't difficult.

Is she really the princess? I don't know.

But is that insignia real? It seems to be.

If I side with the Embroidered Uniform Guard, will that bastard set aside his grudges, extend his hand, and say let's be friends?

Of course not.

"Fire!"

It was a command without context.

However, well-trained soldiers with strict military discipline do not falter or hesitate in the face of orders.

Thud thud thud!

The deafening sound of gunpowder exploding rang out simultaneously.

It was the explosive sound of the steel crossbows, capable of piercing through steel plates, returning to their original form.

Two hundred and fifty iron spears from fifty crossbows tore through the air.

Some were deflected by the weapons, but most burrowed into flesh and bone, shamelessly taking their place.

Some with remaining energy pierced through the body and exited out the back.

To Qing, it looked like something had suddenly flown by, and then the Embroidered Uniform Guardsmen were dancing and collapsing.

However, there were still a few standing.

The one in the front seemed perfectly fine.

From the start, Makseok had stood there nonchalantly in front of the steel crossbows, trusting in the Indestructible Body bestowed upon him as a Unrestrained Realm Master and by the Emperor's favor.

However, his subordinates were anxious, unsure if their bodies, granted a lesser form of the Emperor's favor that made it merely hard to be damaged, could withstand the steel bolts.

So what was the result?

If instructors who taught success studies in Qing's hometown, arrogant con artists who dared to teach success despite having no qualifications or any solid foundation, had seen this, their eyes would have lit up.

Look at this! When you lack confidence in yourself, how can you overcome hardships!

Those with confidence can even deflect arrows with their bodies!

Everyone, the reason I succeeded despite failing numerous businesses is not because of the endless financial support from my parents, no matter how many times I failed!

It is entirely because of my own excellence!

It's not because I quit a large corporation and suddenly had a full bank account while traveling the world!

Just look at this confident and wonderful appearance of this successful lecturer who has completely abandoned everything and has fully booked lecture schedules for a year as a ‘hope preacher'!

Self-assurance! Believe that I will succeed! It is the confidence that believes in certain success that marks the beginning of success. The mind and spirit determine everything!

Now, follow me! I will succeed! I am a go-getter! I am not afraid of arrows! Say it.

Thus, the number of Embroidered Uniform Guardsmen who were still standing was five.

Among them, only Makseok was completely unharmed, without a single arrow stuck in him or any injuries.

This was the difference that confidence made.

And here was another confident person. A great general who trusted not only in himself but also in his subordinates.

"Charge!"

"Waaaaaah!!" "Kill them!" "He said to charge!"

The soldiers charged at once, wielding spears or guandaos.

"Y-You bastards! How dare you! Fine! If you wish to die, I will send you on your way!"

Makseok roared and swung his arm, and the spear shafts were cut in half.

The soldiers of the north quickly retreated and regrouped.

However, even an incomplete Unrestrained Realm Master was still a Unrestrained Realm Master. Makseok, who had been as fast as an arrow, swung his palm, and a fiery dragon wrapped around his arm as he struck a soldier's head.

As a soldier was struck by the palm, he suddenly thought of home.

The smell of rice cooking at dusk, his mother's nagging, his mischievous siblings, and his father with a bad leg, who spoke to his son as he watched-

"Stop the Black Flame Dragon!"

Suddenly, he was suffocated and a hot gust of wind hit his face, while his body was flung backward, leaving him in a dizzying state.

Qing had grabbed the back of the soldier's neck, who was about to have his head smashed by a magnificent palm technique, and threw him back.

Then, Makseok, who was on full alert, stared at Qing.

Qing asked what she had been curious about first.

"Hmm. What is the name of that martial art?"

"……It is the Eighteen Dragon Subduing Palms."

The dragon!

There was the Azure Dragon of the East, the White Tiger of the West, the Vermilion Bird of the South, and the Black Tortoise of the North, with the Yellow Dragon in the center, symbolizing the Imperial Family.

If the Beggars' Union had heard this, they would have been furious.

Not only had the government stolen their martial arts, but they had also changed the name as they pleased.

However, this time, the Imperial Palace had something to say for themselves as well.

The original name was just too treasonous, after all.

A martial art that opposes dragons? Just the name itself was treasonous.

Makseok, feeling disgruntled, answered sullenly.

"Why are you interfering with His Imperial Majesty's affairs, Western Palace? Even if you are the Empress Dowager, do you think you can get away with this?"

The Western Palace served the Emperor's women, so just the name alone indicated that it was the Empress Dowager's faction. However, Qing did not care about such obvious common sense.

"Shut up!"

Qing leaped up and thrust her sword forward.