\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (5)}

With the old woman firmly in her embrace, Qing soared into the sky.

It seems like I've been flying a lot today.

The chilling sensation of floating, the heart-dropping feeling of
succumbing to gravity. But even such experiences, when repeated,
allowed room for other thoughts.

Fortunately, the water's surface was visible below.

She had been worried that the carriage might break down midway, or
that its trajectory might fall short or overshoot, thus landing on the
riverbank instead. But it was a relief that such concerns did not come
to pass.

In truth, Qing was confident she could survive.

She was even confident she could survive if captured by the
Embroidered Uniform Guard.

The ones in danger were Jayu and Yeon Pa.

After all, if Jayu was caught by the Embroidered Uniform Guard, he
would die.

But if the carriage ascended the mountain in a straight line, it would
open a path to survival.

As Qing neared the water's surface, she shouted ‘De-eng!' and exerted
force in the air, flipping her body.

Thus, the three people plunged into the water feet first!

Splash! Their heads emerged from the water.

Qing, in a position similar to backstroke, held the two and paddled.

"Cough, are you alright?"

"Cough, you brat, what reckless thing are you doing, carrying a
precious jade body like that, Your Highness, Your Highness?"

"Wait, check if he's still breathing and don't wake him up yet. I'm
seriously injured, okay? If Jayu starts struggling, I won't be able to do
anything then. So it'll be every man for himself, and I'm going to
abandon him and leave. After all, those who can survive should
survive."

Yeon Pa's mind snapped to attention at that.

It wasn't because she was afraid of being abandoned, but rather
because she was utterly dumbfounded after hearing such absurd
words.

If she had intended to abandon him from the start, she wouldn't have
dragged the carriage all the way here.

She wondered if she should call her a foolish, stubborn, idiotic wench
or commend her for her loyalty.

"Making such insincere remarks. Tsk tsk. Hm, it seems he's just
exhausted and has fallen into a deep slumber."

"What do you mean by slumber? It really is a slumber, but he's just
fainted."

"A noble person does not faint. That is why one should strive to
become noble."

"So what if you call it a slumber with your words? It's not like we can
avoid being soaked by doing so."

Now, all they needed to do was grab onto a large piece of debris from
the carriage and float downstream…….

But there was no wood to be seen on either side.

Why is there no wood? Where did it all go?

It couldn't have all burned up as if it had passed through the
atmosphere or something. But where is it?

However, no matter how much she looked around, there was no wood
to rely on.

As a result, Qing's frown deepened.

She was holding the two with one hand and paddling with the other
arm and both legs.

Every time she moved her limbs, her side protested with intense pain,
causing Qing's expression to contort into a vicious grimace.

Zitan wood sinks in water.

After all, it would be stranger if a material harder than lower-grade
steel could float on water.

Unaware of this fact, Qing was just feeling aggrieved.

Why can't I ever just go comfortably?!

"Are you hurt?"

Yeon Pa's voice was full of concern.

"I already told you that I was hurt from the start. My side was starting
to heal, but now it's probably all torn open again. The fractures in my
bones are probably worse now instead of healing."

"Hmph. Such exaggeration. You're speaking fine, so you must still be
alive. Have you ever really had broken bones? You really can't move at
all. If you try to move even a little, you'll scream and collapse."

"I'm enduring through sheer willpower. You lack willpower, that's what
it is. Willpower."

Qing's swimming gradually gained speed.

It wasn't because her energy was surging, nor because her anger was
rising from the intense pain that felt like lava was flowing in her side.

It was because the current was getting stronger.

Near the middle stream of the Musu River, where the flow was
substantial, the steep slope caused the stream, which had curved
westward at the eroded cliff of Mount Gyeokmok, to straighten and
pick up speed.

"Yeon Pa. It's starting to feel less like swimming and more like
drifting, you know? Can you see any villages or anything?"

The best way to find a village during a disaster was to follow the water
downstream.

The waterworks of the primitive, ancient, and uncivilized Central
Plains were actually quite advanced.

However, that technology was not used to build residences based on
waterworks, but rather to make large cities more convenient.

In this era, technology was an exclusive domain for the noble, not
something to be used by the lowly.

The lowly should just live in discomfort.

They should not dare to become comfortable through technology.

So, if a river with such ample water flow existed, there should be a
village nearby.

After floating downstream for a while, the river turned north where it
met a cliff.

And as they drifted further, rounding the bend eastward, a mountain
range suddenly dropped off, revealing rice paddies on the right,
northern bank.

"There, there's a village!"

It was the most welcome sound she had heard.

Thus, towards the riverbank.

All three were wearing fur coats, which, soaked with water, were as
heavy as a thousand pounds.

Moreover, when one suddenly emerged from the water after floating,
the body, unable to adapt, felt even heavier, pressing down on them.

Lightning continuously struck inside Qing's head.

I really want to tear my side apart.

If it wasn't there, it probably wouldn't hurt.

While thinking how hurt her side would be if she tore it off, Qing woke
up the frail young man.

She slapped him while pouring out all the resentment she felt towards
him for having fainted by himself while she was injured. Slap! Slap
slap!

"Jayu, Jayu?"

"You wench, how dare you strike His Highness's cheek-"

"Ugh, ha, haa. Friend, is that you? Yeon Pa, where is Yeon Pa?"

"Your Highness! This lowly one is here! Are you conscious!? How is
your body?"

"Hmm, there isn't a single place that doesn't hurt. But um."

Jayu gently stroked his cheek.

"I thought I had hit my head on the carriage, but was it my cheek? It's
throbbing incredibly."

At that, Yeon Pa glared at Qing with dagger eyes.

Qing pretended to observe the smoke rising from a distant wildfire.

Thus, the less injured woman and the frail man supported the heavily
injured old woman and headed towards the village.

I hope it's a village and not something else.

If it's a fortified village, it'll really be too much to handle. I'm so
fucking tired.

The villages in the remote areas of Zhongyuan were practically
small-scale warlords that had completed their fortifications.

Naturally, they did not accept outsiders.

However, the open entrance was a welcoming sight.

It doesn't seem like they're completely closed off to outsiders.

Maybe they'll let us rest for a while if we give them all our fur coats.

However, Qing was mistaken.

The entrance was open not because they accepted outsiders, but
because the village was empty.

Everyone had fled because of the wildfire.

This was better.

It would be difficult to deal with those kinds of fortified villages. If they
didn't let us in, they would be an obstacle, and if they did, there was a
high probability they would turn into robbers.

There were several chimneys still emitting smoke.

Did they leave in such a hurry that they didn't even put out the fires?

Even if they were lucky enough for the wildfire to pass them by, the
whole village could still burn down.

Well, that's none of my business.

It would be acceptable to rest here in return for taking care of the
fires.

As such, Qing kicked open the door of a building that was still emitting
smoke and entered.

Then, she heard a startled gasp.

"Wh-Who is it!"

"Oh. Someone was here. Sorry……"

It was an old man with a completely hunched back.

He was startled by the sudden intrusion, but the sight of the river
water dripping from their coats, and their pale lips.

Most of all, the pitiful sight of Jayu, who seemed to tremble as if he
was having a seizure, must have caught his attention.

He immediately offered them a seat in front of the fire, covered them
with blankets, and served them bowls filled with hot tea.

Hot water was indeed the best for raising body temperature.

As the hot tea entered her cold and aching body, she felt a blissful
sensation as if her entire body was melting and unwinding.

"Phew, thank you."

"I thank you for your kindness."

"Were you perhaps hunting? You have swords, so you must be martial
artists? Well, what does it matter with a wildfire on our hands. Did you
see the fire and jump into the water?"

"Well, something like that."

The soldiers' bandit attire would evoke such a response from ordinary
people.

After all, bandits were dressed like beggars living in the mountains.

They didn't go around wearing high-quality fur coats, fur hats, and fur
shoes.

"It seems the villagers have evacuated. You're still here, Elder?"

"I've always lived here, where else would I go? Besides, my old woman
is buried back there, how can I leave her alone to burn? I think it's
about time I went to see her."

"Ah……"

"Anyway. You saw the wildfire. How was it?"

Jayu and Yeon Pa looked at Qing.

One of the characteristics of isolated fortress villages that lived
without any connection to the outside world was their terribly
distorted dialect.

It was a dialect that had transformed over a long period of time,
isolated among themselves, and was practically a foreign language
with only a few understandable words here and there.

But for some reason, Qing understood it perfectly.

However, it seemed that Qing hadn't realized that it was strange for the
old man to understand her perfectly when she was the only one
understanding him.

It was because people generally assumed that if they understood,
others would too.

"The government soldiers set the fire."

"Ehh. What? It's not time for that yet."

Suddenly, the old man started packing his belongings busily.

Qing was puzzled.

"Didn't you say you wouldn't leave your wife behind?"

"I can die to fire, but I can't die by the fire set by those government
bastards. Those fucking bastards! Those despicable sons of bitches! I
hope those government bastards get their flesh minced and fed to their
parents, cutting off their lineage! I can't die at the hands of those
government bastards."

He could die in a wildfire, but not in a fire set by government soldiers.

The curses were similar in dialect.

Government bastards, mincing their flesh, feeding it to their parents,
cutting off their lineage.

The old man's view of the government and the authorities was fully
revealed through his words.

Yeon Pa, who had been listening, was appalled by such dreadful
irreverence.

"Y-Y-You, old man."

"Enough."

Jayu, who stopped Yeon Pa, had a dark expression.

The old man finished packing and left, and now only the guests
remained in the house without an owner.

"It's just as well. Jayu, you should rest. Drink some more hot water and
once you've warmed up, take off your wet clothes, wrap yourself in a
blanket, and stay put. I'll look for some dry clothes and food. Yeon Pa,
can you help me?"

"Aigo, I can't go."

"What do you mean? Earlier you said I was exaggerating, but now you
say you can't go?"

"What? Aigo, this young wench is trying to boss around an old woman.
My entire body is torn and bleeding, but I'm supposed to move around
like this? I'm an old woman trying to catch a break."

"Ah. Right, you did say that. I'm sorry. Yeon Pa, you should also take
off your wet clothes and dry them while resting. I'd like to take a look
at your wounds right away, but I need to find some clean cloth to
bandage them. Ugh."

Qing groaned as she stood up.

Her body was heavy, her whole body ached, and her side felt like it
was filled with hot, burning nails instead of blood, but…

If she didn't do it, Jayu would freeze to death or fall ill from the cold,
and Yeon Pa also had torn wounds, so what could she do?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In fact, Yeon Pa really thought Qing was exaggerating.

She claimed that her muscles were torn and her bones were fractured,
but if that were truly the case, she wouldn't even be able to sleep
properly due to the pain, let alone move.

Yet, here she was, having dragged the carriage that far and swum for
nearly half an hour while holding two people. So how could she be
injured?

But as Qing unwrapped the bandages pressing against her wounds,
Yeon Pa let out a groan.

"You, you, you wench, in that state."

Her right waist was caved in like a gourd, while her left side was
swollen outwards, making her look like a pregnant woman with a child
on her side.

The bruises, which had subsided and turned black, had burst again,
with new purple bruises forming over the old ones.

The dark bruises with fresh purple ones on top were bumpy and
unsightly.

"How, how could you move around in this state!? How, you, goodness.
What do I do."

Yeon Pa was at a loss, making sounds of lament and reaching out her
hands only to withdraw them, unable to touch the wounds.

"If you're this hurt, you should act hurt. I didn't know and, goodness,
this old woman's eyes were clouded."

Then she fretted, not even hiding her remorse.

Qing chuckled at this, but soon her expression changed due to the
pain.

"I'm used to it because it always hurts. And I can't just lie down
because I'm in pain. Besides, it's normal to not feel the pain when
you're in a fight, even if you get stabbed or cut."
