\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (6)}

How could a person be so severely injured yet remain so calm?

Yeon Pa, filled with pity, looked at the grotesquely swollen and uneven wound, then back at Qing's face.

At that moment, it felt as if she had been hit hard with a hammer.

How could she have only just noticed the way Qing's eyebrows were furrowed and the corners of her eyes trembled?

She thought the girl's expression was merely sullen, but of course, she couldn't keep a straight face when she had been foolishly enduring pain all this time.

This old woman had been so thoughtless, making this poor child do all sorts of things for her.

It was not the time to be attending to the Prince.

Rather, it was time for the Prince to be the one nursing her.

And to think it was that Prince of all people.

Yeon Pa's feelings of guilt reached a point where she even thought that the Prince she cherished most in the world, the one she held most dear, should be the one nursing her.

Yeon Pa's expression was drenched in regret.

However, Qing's eyesight wasn't in the best condition to be examining people's expressions.

So, whether Yeon Pa was making a fuss or not, Qing applied medicine to her side, placed a large piece of cloth over it, and suddenly pulled a bandage tightly around her waist, causing-

"Aaaagh!!"

She couldn't help but scream out loud.

The wound had to be pressed tightly all over, but it was a festering wound that had burst open again after being imperfectly healed. Thus, the pain was inevitably going to be intense.

Qing collapsed, curling up on the floor, gasping for breath as she trembled violently.

Startled, Yeon Pa cried out.

"Wh-What are you doing?"

"What's going on?!"

Following the terrible scream, Jayu burst through the door.

Qing was tending to her wound, wearing only her undergarments.

Jayu's eyes caught sight of Qing's pure white back as she bowed deeply to Yeon Pa.

It was so white that it was almost blinding, without a single blemish, as if it had been carved from the finest white marble. It was truly a sight that could steal the breath of any man, causing Jayu to inhale sharply.

But then, his gaze fell on the hideously swollen lump of flesh on her left side, and his expression instantly hardened.

"Yeon Pa? How did-"

"Your Highness!"

Yeon Pa quickly blocked Qing's back.

"How could you so carelessly enter a room where a woman resides! You should leave immediately!"

"Ah, uh, um. I apologize, I apologize."

Jayu was utterly bewildered.

It was the first time he had ever seen Yeon Pa angry.

Yeon Pa was someone who would have praised him, saying, "Oh my, our Prince, you have such a manly spirit" or "Even covered in blood, you look so wonderful", no matter what he did. Even if he had harmed someone.

So, he couldn't help but panic at her fierce glare.

Jayu stammered as he retreated, respectfully grabbing the door he had kicked open and stepping over the threshold.

Then, as if suddenly remembering something, he asked through the not-yet-closed gap in the door.

"Uh, if I may, it seemed like my friend's condition was not good. Perhaps-"

"Close it!"

It was unclear whether she meant the door or his mouth, but it was a sharp order either way.

Unable to ask which one, Jayu just closed both.

Only then did Qing manage to get up.

"Haaah, wow, I almost died-"

"You child! What are you doing?!"

Yeon Pa shouted, and Qing tried to explain.

"Haaah, hoo, hoo. I have to tie the wound tightly to be able to move. If I move around with it loose, I'll really collapse on the spot, unconscious."

"Khm."

"I can't do this alone. I'm glad Yeon Pa is here. Could you help me a little?"

"Glad my ass, aigo, you child……"

The one who was glad was actually the Prince, who met Qing in a situation where his life was on the line, and Yeon Pa.

After all, if the poor child had just passed them by, she wouldn't have had to suffer such a terrible ordeal.

However, that didn't mean they could just let the wound heal on its own.

The west wind was blowing, and although the forest fire wasn't spreading too quickly, who knew why the villagers had abandoned their homes and fled?

It meant that the village was by no means safe.

So, Yeon Pa carefully pressed down on the cloth.

"Ugh, a little tighter. No, a little, just, more, more, more, haaaagh."

"A-Are you okay?"

"I'm not okay, but you need to apply more pressure."

Even if it hurt, it was better to do it quickly in one go.

However, the person assisting her was hesitant and couldn't quite apply the necessary force, so the process was dragging on.

Ah, seriously. Just do it in one go.

And what's with her?

Why is the original foul-mouthed granny suddenly acting like a real one?

Of course, the original foul-mouthed granny's curses were full of affection, but still.

Are old people usually weak in front of patients?

As such, a procedure that could have been over with one sharp pain ended up being long and very painful.

Qing gently shook her body, feeling the pressure.

Ugh, the sharp pain was like a nail being hammered all the way to the head in one go.

But still, I guess this is bearable?

At least to the extent that my vision doesn't turn white, leaving me unable to do anything but tremble, nor is my breath so caught that my body automatically curls up.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The seventh of the Eight Blood Swordsmen of the Embroidered Uniform Guard, called Gye-du, was flung to the ground by Qing's underhanded tactics.

To be precise, he charged towards the earth like a human arrow.

In a way, one could say that a human had challenged the earth itself.

However, the result was a complete defeat.

It was a reminder that humans could never win against Mother Nature, with his nose ending up crooked.

In fact, it wasn't just his nose.

As he scraped his face on the ground, frozen solid in the twelfth month of winter, his nose was misaligned and his entire face was marked with long, black scabs, as if black rain had fallen.

However, the reason his face wasn't completely torn apart was thanks to the grace of His Imperial Majesty, the sole sovereign, which could be attributed to the Imperial Grace's Divine Blood Technique.

At any rate, with their leader knocked unconscious on the ground, the Embroidered Uniform Guards were deep in thought.

If they reported that they had missed that runaway rickshaw and its passenger, he would surely throw a fit.

It would be fortunate if he just got angry; that bastard was the type to lash out at his subordinates with a horsewhip.

Originally, he wasn't such a brutal superior.

However, after becoming one of the Eight Blood Swordsmen, his personality became more violent as his realm increased.

The Embroidered Uniform Guards said among themselves that people's true nature comes out when they rise in status. They believed he was a dirty bastard who had been holding back and had finally revealed his true colors.

So if they said they missed them, he would surely throw a tantrum and make a fuss.

Then what?

They wouldn't miss them.

The Guards agreed.

They would say that the rickshaw, unable to slow down on the steep mountain road, plunged down the southern cliff.

However, their efforts were in vain, as Makseok soon regained consciousness and started throwing a tantrum.

"How could eight, eight of you be beaten by just those bastards!? Is this the standard of the Embroidered Uniform Guard? Ha, I can't believe it! You weaklings!"

The faces of the Embroidered Uniform Guards turned sour.

Six had died and two were seriously injured, yet instead of mourning, he was angry at them for being beaten.

Moreover, it was the healthy and alive Guards being called weak, not the ones who had already died.

And above all, he himself had been knocked out, unable to catch a single rickshaw puller, despite being their leader.

Makseok, too, was furious at his subordinates' attitude.

"The subordinates of that Lee fellow show respect even to a mere General, that lowly farmer's son, yet how dare you be so disrespectful to me, a scion of a noble family and the seventh of the Eight Swordsmen, personally appointed by His Imperial Majesty!"

At that moment, the Guards had a great realization.

So that's why he hated General Lee to the core; he was jealous, they thought.

However, respect could not be demanded through status and rank.

Respect could be bought with status and rank, but true respect had to come from the person's heart.

Just shouting, "Respect me!" wouldn't suddenly make the Guards feel respect.

Especially not when it was coming from someone with a crooked nose.

Makseok, fuming by himself, eventually turned away in a huff.

That fucker is sulking again, the Guards thought with tired expressions.

When Makseok sulked, he wouldn't give any orders and would just glare with his eyes wide open, acting like he was testing them to see how they would do without him.

So, the Guards decided to continue what they were doing.

But what were we doing again?

Right, we were on our way home.

Then, the Guards' hearts were suddenly filled with burning rage.

If that rickshaw had just passed by, none of their colleagues would have died, and above all, they wouldn't be going through this hardship.

It was no big deal that four of the dead were scheduled for promotion.

It was because those who were always eager to be seen by Makseok, thus drawing everyone's displeasure, were the ones who had their promotions set in stone. As such, the Guards did not particularly feel a sense of loss or regret.

Thus, the Guards climbed down the mountain and, since the forest fire was chasing them, they crossed the river.

"Ha, those idiots. They'll head north anyway, but they crossed the river so early. They must be fools who soak their bodies crossing every time the river bends. Let's see how many times they cross."

Makseok mumbled, making sure everyone could hear him.

It was a familiar yet annoyingly unpleasant attitude.

However, Makseok's words weren't entirely wrong. After avoiding the mountain slope on the other side and heading north, the very Wushui River they had crossed earlier curved back to block their path again.

Moreover, since the Wushui River wound around the cliff and flowed northeast, they would have to cross the river twice more.

Damn it, if only he had told us earlier.

The Guards crossed the river again, and then once more.

After doing so, they saw a fortified village with several plumes of smoke rising.

With the cold river wind blowing, their wet clothes had frozen stiff, making their teeth chatter.

The Guards' faces lit up as they headed for the closed gate (which Qing had closed and barred on her way in). Then, that bastard loudly mumbled again.

"Looks like they're so relaxed that they want to rest in such a den of lowly commoners? The forest fire could spread at any moment, yet they're not just resting but settling down. Seeing how they're like wet mice, that beast's den must suit them well."

The Guards' foreheads all bulged with veins.

If it weren't for the fact that he was a Master, they would have beaten the shit out of him and stabbed him long ago.

Surprisingly, the reason they didn't stab him wasn't that Makseok was their superior.

After all, throughout both the East and the West, the number one cause of death for leaders of combat units was being betrayed by their subordinates.

The Guards reluctantly bypassed the village with a sense of regret.

However, seeing the rising smoke, Makseok, too, craved a cup of hot tea.

So, after bypassing it, he loudly mumbled while looking at the wide-open north gate of the fortified village.

"Ha, despite having injured men, they don't even think about treating them. Is this what they call camaraderie? I knew they were undignified bastards from the start."

The Guards' foreheads bulged with veins on both sides.

It wasn't a good sign.

Usually, the third vein was expected to bulge on the entire body of an unlikable superior.

Thus, the Embroidered Uniform Guards set foot in the village.

The injured were placed in a building where smoke was rising, and lots were drawn to decide on a search party. As they gathered to prepare, he mumbled once again.

"There's no one at the south gate, which is closed, and the north gate is wide open, which means they ran away at the sight of the forest fire. Since they even left the fire in the hearth burning as they fled, there are probably only a few frail old people left, if any. Are they really that afraid? Is this truly the attitude of warriors serving the Emperor? My heart swells with pride."

It was truly annoying to hear him mumbling while they were drawing lots.

If they hadn't drawn lots and just sat around, he would have mumbled about how they weren't even going to scout the unfamiliar land.

Since it was an action done for show in the first place, they didn't really count this against him, this time.

Thus, the Guards lit a fire to make it stronger and took off their wet clothes, hanging them to dry as they took a long break. 