\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (13)}

The biggest demerit on Qing's evaluation sheet was her lowly birth.

But Qing's lowliness could be elevated by the Prince.

When Yan Pa said that a woman of low birth could rise through a good marriage, she wasn't just being a matchmaker, but speaking from her heart.

But what about the Prince who accepted Qing?

How could he bear to see people pointing fingers at his beloved for keeping a lowly person by his side?

But what if it turned out she was a princess!

Moreover, a legitimate daughter of the Imperial Family born from the Empress, and had already received the title of Princess.

So Yan Pa was all smiles, thinking that if such noble bloodlines were to unite, they would be the most noble couple in the world.

The fact that the two were third cousins was of no concern to Yan Pa.

In fact, in Zhongyuan, marriage between those with the same surname was forbidden.

The scholars of the world would rise up and point fingers, arguing that those who engaged in such acts were no different from animals. (Animals might feel wronged by this)

However, to the people of Zhongyuan, the law was something to be broken, and those who followed it were mocked as fools.

This was one of the characteristics of the Chinese people, a spirit that their descendants in the future would also embrace and practice.

So no one followed the law.

Moreover, the law of Zhongyuan had never, not even for a single moment, stood above those in power.

This would remain the same in the future, where there was an opportunity for it to stand above, but nothing happened.

Thus, the law of Zhongyuan was forever destined to be a sword-wielding slave of the powerful, an executioner that only beheaded the weak.

So what could the people of the world possibly do?

If the Prince were to marry a Princess, even if the lowly people dared to whisper, they would only lose their heads.

After all, it didn't matter if those of noble birth didn't follow the law.

Additionally, it was a very welcome event for Yan Pa personally.

In traditional Chinese culture, people with the same surname lived together in villages, marrying amongst themselves.

Occasionally, they would raid neighboring villages to abduct women, slaves, and loot grain.

Even now, remote villages fortified in the mountains were composed of people with the same surname, essentially forming a community where neighbors and cousins were indistinguishable, a true community of close-knit neighbors.

This was Yan Pa's background.

Thus, rather than marrying someone she knew nothing about, even their background, personality, and everything, she believed that a marriage between relatives who had known each other since childhood was a match made in heaven, where they could trust and care for each other for a hundred years.

So, all the better!

Yan Pa was simply overjoyed.

So happy that she didn't even feel the pain from the wound that had been torn, pierced, stitched, and then burst open again before being stitched once more.

This old bag of bones shouldn't be doing this!

"Princess, it is not befitting for such a noble person to do such a thing. Let the lowly one pull the cart, please rest your noble self."

Qing suddenly got goosebumps.

What's this? Why did the vicious mother-in-law suddenly become a housekeeper?

"No, I keep telling you, I don't know if I'm a princess or not? The Empress just, um, it's a really bad thing to say out loud, but anyway, she might have been mistaken."

"Just by looking at one's physiognomy, a noble person naturally has a noble aura. This lowly one can see that the Princess is undoubtedly of the Dragon's lineage, so there is no reason to doubt further."

For Yan Pa, the truth was no longer important.

If she was a real princess, then she was a princess.

And since the Empress had already vouched for her and given her a token, even if she was a fake princess, she just had to become a princess.

Qing was dumbfounded. Of course, she was.

"No, just an hour ago, you were talking about lowly this and that. Is it okay to change your words so suddenly?"

"This old one was blind and failed to recognize a noble person, so I will accept any punishment. However, even if you cut off this old and lowly one's head, your inherent nobility will not disappear."

"Ugh. This is driving me crazy. Fine, get back on."

"How could I dare to ride in a cart pulled by a Princess? If I didn't know, then so be it, but now that I do, it feels like sitting on pins and needles."

Qing's forehead creased with a frown.

"Ugh. And I even modified it to make it comfortable for you to ride in?"

"It is not about the ride's comfort. It is this lowly one's heart that feels that way."

"Fine, whatever, okay? Since I'm a Princess, it's an order, so get on. If I have to make an old lady who's about to keel over pull a cart, what would that make me?"

Qing was naturally weak towards the elderly, and her background prevented her from doing such a thing.

It was like making an old lady, who was picking up scraps of paper for a living, push her own cart for her.

And this old lady had holes and tears all over her body, almost on the verge of vomiting blood.

(But the old lady was a Supreme Master of the Unrestrained Realm)

"If that is your wish, I shall obey your command."

Tears welled up in Yan Pa's eyes.

The reason Yan Pa had secured her position in the Prince's manor was not just because of her martial prowess, but also due to the mountain-like grace of accepting even a lowly, demonic old hag like her as family.

And now, she saw that the Young Lady was also a person with such a beautiful heart.

A full ten thousand points to her endless compassion and kindness, even to those beneath her.

No, how could a lowly person dare to score such a noble being? How impudent.

If Choi Leeong were to score Qing, he probably wouldn't be as generous.

Following the Purple Lightning Demonic Warlord, the Wheel-Turning Demonic Witch's affection was also pouring out. As such, Qing's ruthless slaughter of the elderly showed no discrimination between good and evil.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Jayu hadn't received the title of Prince yet and was still called Deokhyeon, thus residing in the Imperial Palace, his hobby was reading the words of sages, a pastime that truly suited his ink-fragrant appearance. So, as he was once again enjoying his hobby under the guise of studying…

……Aigoo……Young Miss……Doing this……Please……Your dignity……Please……

Suddenly, the outside became noisy. And then, the door was thrown open with a loud bang!

"Uncle! What are you doing!? Let's play!"

Leaving aside being a prince, this was a woman who dared to open a man's door without any fear.

She had a tall stature and a beautiful face, but her chest was so large that it made her look foolish and shallow, truly the image of a temptress who would barge into a man's room without hesitation.

But there was a mitigating factor to consider.

Although her body was that of a woman, her mind was that of a mere ten-year-old child.

"You brat. Have you snuck out again?"

"I'm bored. Let's play."

"Ahem, where did you learn such lowly speech-"

"I'm bored! Let's play!"

"Isn't it time for poetry reading with your tutor right now-"

"Is that important? I'm bored, I said?"

This, this is a lost cause.

Jayu shook his head slowly.

Originally, to a ten-year-old child, boredom was the most serious of problems. So the fact that it was time to recite poetry in front of a scholar was not an important matter at all.

"If you're bored, there are other nieces-"

"They're no fun. Why would it be fun to just sit still and wiggle my fingers? Let's have a sword fight instead. A sword fight."

"Ahem, if it's a sword fight, shouldn't you find someone else other than me-"

"Uncle is the weakest person I know. Even if I don't go easy on you, you're the only one I can take on. It's no fun with people who go easy on me. I'm gonna beat up my uncle."

Although it was true that Jayu was physically weak, was it really appropriate for a child to say this, no matter how young and honest they were?

And did she just say she was going to beat me up?

"I didn't say that. I want to play with my uncle."

"You definitely said that."

"I didn't."

"You definitely said you were going to beat your uncle up-"

"I didn't."

As his words kept getting cut off, even Jayu felt a surge of irritation.

If it were up to him, he would have given her a good smack.

However, as an elder, Jayu endured.

Not only because he knew he would lose in a fight, but also because fighting with his niece would make him look foolish, regardless of whether he won or lost.

"Hmm. You don't like sword fights?"

"How about calligraphy instead? Some good paper has just arrived."

"Hnngggg."

His niece pretended to think for a long while.

And then, she finally came to a conclusion.

"No. Oh, right. I'm hungry. Uncle, I'm hungry."

"Then I shall have snacks brought up immediately-"

"No, I have sweet potatoes. Let's eat sweet potatoes."

"What?"

What was this sudden talk of sweet potatoes?

Perplexed by the abrupt remark, Jayu looked at his niece.

But had she always been this beautiful?

Why does it seem like she's grown three inches taller in the blink of an eye?

Huh? Isn't that niece Qing, my friend?

Suddenly, the woman who had turned into Qing dashed into a side room of Jayu's quarters.

"Friend, why are you going into the servant's quarters?"

Well, whatever. I can't stop her anyway.

Jayu smiled wryly and headed towards the servant's quarters, opening the door.

Then, Jayu's eyes widened.

There it was, a dazzlingly beautiful back.

Among the countless lines that a woman's body could create, it was as if only the most beautiful and precious had been gathered to form it, a white back so beautiful it took his breath away.

Both arms were raised high to tie up her hair.

And under her armpits, even though he was looking at her back from behind, how could those fleshy mounds on her front peek out and reveal their presence so distinctly?

Jayu stared blankly at that back, forgetting even to breathe.

Motionless, he stood there for several hours, just gazing at it, until…

The woman suddenly spoke as if she had just remembered.

"Ah, Friend. Sweet potatoes. Do you want to eat sweet potatoes?"

Only then did he notice the horribly rotten sweet potato, swollen to the size of a pumpkin, that was attached to her side-

"Gasp!"

Jayu sprang up.

"Water, bring me some water."

His mind was dizzy and he called for water, but there was no response, no servant to bring him his bedside water.

Only then did he come to his senses. Ah, that's right, I'm not in the royal household, he realized.

"Haa. What kind of dream was……"

Then, a sense of shame washed over him.

Niece, it was his niece.

Gazing at his niece's back, yet how could he lose his senses at such art. Indeed, it was truly beautiful-

Jayu's eyes suddenly lost focus.

And then, just for a moment…

"Ahem, ahem."

Blushing, Jayu cleared his throat and abruptly lay back down on the bed with a thud.

When he closed his eyes, he could see that white, smooth, fair skin, like the moonlight.

"I must be, I must be going crazy."

Jayu looked around and saw the water bottle on the table. Forgetting his dignity, he gulped it down directly from the bottle.

As the cold water filled his stomach, he finally regained some of his senses.

This won't do.

What was the reason people were human?

Jayu was someone deeply engrossed in the words of sages as a hobby.

How could he, with his niece, such, such an outrageous, no, it can't be, the smooth curve along the spine, the neatly protruding skeletal frame, the shadows of the ribs clearly visible under the armpits, and the weighty presence revealed to the left and right, aigh, this is all because of a demon! It must be a demon!

Jayu's face turned red, as if it would explode, at the outrageous thoughts he had conjured himself.

However, Jayu's aesthetic sense, well-versed in calligraphy and painting, could not help but admit that it was the most beautiful back that had ever existed and would ever exist, a work of art-

Clang! Jayu slapped his own cheeks roughly and even poured the water bottle over his own head.

Drip……

However, since it was a narrow-mouthed bottle, the water just drooped down his head powerlessly. 