\chapter{Always Be Careful of Fire, and Check Again Even After It's Out (1)}

Several months ago, an order came down to conscript useless, skilled soldiers from each army.

The commanders gladly gathered the trash and sent them off.

One might wonder what useless, skilled soldiers meant.

But the thing was, soldiers' monthly wages increased very slightly with each passing year.

Though the increase was minuscule, it was still an increase.

The question was whether they were worth the increased wages.

Surprisingly, soldiers were most loyal and obedient during their first year, when they were still recruits.

As they gained experience, they would start to shirk their duties with various excuses, and not only would they shirk alone, they would try to get their entire squad of ten to do so as well, using all sorts of tricks.

It wasn't as if they became skilled veterans like the ‘real soldiers' of the Northern Army as their years of service increased. So, keeping them around was nothing but a loss. They were just garbage who thought lightly of orders and passed on their tricks to others.

Thus, the battalion commanders made secret deals to get rid of such waste.

They would kill each other's waste.

Moreover, if a soldier died during an operation, compensation could be added to the budget.

And since this compensation money did not reach the bereaved families, disposing of waste was even economical.

Did the higher-ups not know about this situation?

It was an operation to assassinate a prince.

If it succeeded, they would silence the mouths of those involved, and if it failed, they would be executed.

So, it was decided to use incendiaries.

It didn't matter if they were going to die anyway.

It was also convenient because there was no need to execute them one by one.

But it wasn't like all the armies of the country were like this.

Outside the fire zone, there were real soldiers.

The Northern Army!

The hardened soldiers who trained through endless battles with the barbarians in the north.

They were granted proper martial arts, sufficient salaries, ample supplies, and even significant advantages for their children's future, making their loyalty unwavering.

They were some of the few soldiers in Zhongyuan that could be called elites.

Such soldiers were treated with great care from the start.

So, behind the fire zone, where trees and leaves had been cleared and the ground overturned to prevent the fire from spreading, the real soldiers lay in ambush, not to be burned.

It wasn't just about using incendiaries.

Search and destroy operation?

What search and destroy could be carried out with these pieces of shit who lacked any semblance of military discipline, who tried to avoid, hide, and pass off any duty?

They would just get caught immediately, which would be the same as letting the enemy escape.

The Northern Army couldn't be deployed due to their low numbers, and losing them would be detrimental to the nation's valuable assets (this was important).

But how convenient would it be to just set a fire?

If the waste burned to death, then even better.

Even if they survived, setting fires on three sides would force them to emerge from one side, where properly positioned elite soldiers could finish them off.

Thus, the soldiers within the fire line, who were casually patrolling and pretending to search the mountain, were essentially acting as a signal or a beacon.

If a bloodbath occurred inside…

For whatever reason, whether they joined up with missed guards or an injured old man waged a desperate battle to the death, it meant that the prey had considerable strength.

Then, regardless of the state of the fire line, they would just set the fire.

After all, if the fire spread, what was the big deal if a few lowly beings burned to death?

The man wearing a Gedu helmet laughed.

"Initiate the incendiaries. The prevailing wind is from the west, right?"

"Th-The geomancer said that there could be a north wind or a southeast wind."

When the prevailing wind was from the west, the weather became warmer.

When the temperature rose, it meant one of two things.

Either a cold wind would descend from the North Sea, or, although rare, a hotter wind could blow in from the South Sea.

At this, the Gedu man burst into laughter.

"A southeast wind, you say? Hahaha! Is that geomancer's surname Zhuge, by any chance?"

It was an outright mockery.

In fact, the weather forecasting in the primitive, ancient, and uncivilized Zhongyuan was just a collection of statistics accumulated from experience, so its accuracy was not very high.

(Though Qing's homeland was similar, they had vast amounts of diverse data and exceptional computing devices to perform the calculations.)

"Give us four, no, three more days-"

The army general's earnest plea was cut off by the Gedu man.

"Do it now."

"But if the fire spreads, the people will suffer great losses. We are the Emperor's army, tasked with protecting the Emperor's people-"

"You fool!"

Thwack, the Gedu man's palm struck the general's head.

The blow, infused with Inner Qi, sent the helmet flying, and the general staggered, barely managing to regain his balance.

"Hah, you stupid fool. You are the Emperor's army, and you are not protecting the Emperor's people, but the most noble Imperial Family. Only the Imperial Family. Hey, Zixing. You there."

"Yes, Great Commander."

"Suppose there are traitors right there. What should the army do?"

"……They must be pursued and killed."

"Hmph. You're too soft. I expected more because I heard you were talented, but you won't make it to the top. Is it because you're from a lowly background?"

The general gritted his teeth.

The statement that he wouldn't make it to the top was a declaration that his promotion would end here.

"Go and set the fire. Consider it fortunate that the traitors are not hiding in the city. At least you won't have to burn down a city."

"Understood."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As Qing lay flat on her back, listening, she suddenly saw a red glow flickering at the edge of the sky.

Qing was bewildered.

What's that? Dawn? Did I doze off?

But why is the dawn rising in the west?

Is the sun really rising in the west?

Is it some kind of event in this primitive, ancient, and uncivilized Zhongyuan where they make the sun rise in the west on certain days?

When discussing the wind, saying ‘west wind' meant a wind blowing from the west, not towards the west.

Therefore, in winter when the prevailing wind was from the west, if incendiaries were to be used, it was obvious to set fire to the west first.

There's a saying, ‘The flames pierce the sky'.

It means that the firelight pierces the sky, referring to a large fire or such a force.

Qing frowned, trying to focus her vision, wondering what the principle behind it was and whether it was the aurora she had only heard about.

Then, after a short while…

Ah. It's a fire. A forest fire.

Hmm? Isn't that a good thing?

I should probably hide in a cave or something, or maybe dig really deep into the ground and hide there.

It was a thought that came naturally to someone of Qing's background.

Since people in Qing's homeland did not live among mountains and forests, they did not know how terrifying a forest fire could be.

When a person was caught in a forest fire, the hot air would damage their lungs first.

This hot air was more than twice as hot as boiling oil, so with just one breath, the airway and lungs would be instantly cooked.

Moreover, the spreading speed varied with the wind, but it was comparable to the speed of a running horse, or even twice as fast with a strong wind.

The people of Zhongyuan knew the terror of these forest fires, calling it the work of demons, referring to it as the Fire Demon.

If they hid in a cave, they would be found not as Qing, but as a well-done roast. Even in a deep cave, there wouldn't be enough air to breathe, suffocating them like drowning outside of water.

Even if they dug into the ground, they would just end up like Peking duck, not Peking Qing.

"Yeon Pa? It looks like there's a forest fire."

"What?! We must flee at once! Your Highness, Your Highness, you must wake up!"

Yeon Pa turned pale, shaking the prince awake.

Just by looking at how she was shaking the body of a prince she cherished so dearly, one could tell how urgent and flustered she was.

"Yeon Pa? There is no need to rush like tha-"

"What are you talking about?! The Fire Demon, the Fire Demon is coming! It's approaching us!"

"It is still far aw-"

"You foolish woman! The Fire Demon approaches faster than the gallop of a steed! It will engulf us in an instant! Your Highness, get on the cart at once!"

It was a small cart Qing had taken from the army's temporary camp.

Because of her side, she couldn't carry people.

The moment someone being carried flinched and squeezed her sides, Qing would be unable to withstand the pain and would end up rolling on the ground.

If Qing ran at her speed and rolled, the person being carried would suffer at least minor injuries, if not severe ones.

Carrying someone on her front would tie up both her hands, and carrying them on her shoulder would prevent her from making vigorous movements.

It would be a strange form of Iron Mountain Stance, destroying the organs of the person slung over her shoulder.

And there were not just one, but two pieces of baggage.

If Qing were fine, she could have wrapped one on her back and one in front with a cloth and broken through, but…

Then she saw the cart.

It was just the right size for those who collected scrap paper in Qing's hometown to pull around.

When Qing saw it, she thought she could just put the baggage in it and pull it along.

"Don't rush and tie it securely, so you don't get thrown off. You too, try to stay as low as possible."

"Why are you so calm!"

"If you rush, you won't get things done, you know?"

As Qing said this, she adjusted the harness around her chest and under her armpits.

Hmm, there's an obstacle here, so it won't slide down to my waist and squeeze my sides.

But it's still a bit uncomfortable.

A human horse? Can I even call myself that? When there's a perfectly good horse. I wonder how Wang Goongdung is doing. Horse, horse meat, I want to eat horse meat sashimi…….

"Now, let's go quickly!"

"Hold on tight! Since we're going on an uphill road, it's going to be very bumpy!"

Thus, Qing started to run.

A woman pulling a cart carrying two people would have made even a street peddler stop and stare in awe at the spectacle.

Moreover, she was running uphill, pounding on the rugged mountain slope.

If people had seen it, they would have rushed to buy the medicine, claiming it must be the medicine that made Xiang Yu the Conqueror, emptying their gold to do so.

Shut up and take my money!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The level of weather forecasting in Zhongyuan was poor.

It might rain, or it might not.

As for the exact probability? Well, since it hasn't rained much lately, it's probably quite high?

Or maybe not. How can humans comprehend the will of the heavens?

Therefore, geomancers predicted the widest possible range.

The prevailing wind is from the west now, but a north wind might blow, or a southeast wind, and then it might rain, and although it's not cold, there's a slight possibility of snow.

This way, they were bound to get at least one prediction right.

That was how geomancers avoided taking responsibility.

Of course, because of these kinds of shallow tricks, when there was a drought or a major typhoon, the geomancers were the first to be hanged.

However, the geomancer should have been more imaginative.

After all, he didn't say that the prevailing western wind could become stronger.

As the night deepened, the prevailing western wind suddenly howled fiercely, developing into a violent gale that shook the forest.

If the wind was strong, the embers would spread faster and farther.

Thus, the embers, carrying sparks and heated leaves, easily jumped over the ten-foot wide barren strip that people had laboriously overturned.

It was exactly where the geomancer had insisted that twenty feet should be cleared to be safe.

He was actually a quite renowned geomancer.

The fire blazed up.

The enormous Fire Demon rushed forward greedily.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Thump, thud! Clunk!

A hand-pulled cart was climbing the mountain at an unbelievable speed.

The cart was more akin to flying than rolling along.

This was because the time the wheels spent in the air was far longer than the time they spent touching the ground.

The ratio was roughly one to nine, so it wouldn't be wrong to say that the cart was practically flying.

The two people riding in the first flying cart of Zhongyuan were having a miserable time due to the rough ride.

Zi You was fine, but he didn't know any martial arts. On the other hand, Yeon Pa was a Master, but she had many holes in her body and was covered in wounds that had been stitched up.

So they could only hold onto the safety ropes tied to various parts of the cart, bouncing around helplessly.

At least they were wearing three layers of coats and three hats, so they could endure the bumping and bruising.

Qing, too, felt the movements of the baggage bouncing around inside the cart.

"Just a little more! We just need to reach the road above!"

Then the left wheel hit a large rock, and the cart tilted sharply.

Qing gritted her teeth, lifted her left hand to grab the handle of the cart, and yanked it down! Her ribs screamed! The three muscle sisters on her side screamed as well! The pelvis below them cried out that the mountain was there! Just kill me already! Aaaaaagh!

Suddenly, her left leg lost all strength.

It was an inevitable physiological response.

Qing bit down hard and stomped her right foot, hopping, one, two, three, four, five.

"Ugh……"

The world seemed blurry, but it wasn't because of her eyesight.

It was because of the tears that had welled up from the intense pain, blurring her vision.

But it didn't matter much whether her vision was blurry or not, since she couldn't see well either way.

Just one more small hill to cross and there would be a road, at least one where the cart wouldn't shake.

"Run, run away!"

"The fire is spreading! Run quickly!"

As soon as they crossed the ridge, they saw a group of bandits running down the road, suspiciously dressed in high-quality fur clothes, pretending to be bandits. 