\chapter{Who Would Threaten With A Sword… (5)}

Qing pushed her True Qi through the pressure points of her lower body.

Her legs, clogged and poorly circulating Qi and blood, felt numb and lacked strength.

Yet, a little of the True Qi from the Yue Maiden Cultivation Technique managed to get through.

It was like blocking one nostril and forcefully blowing air through the other.

The excessive force caused a mild aching pain from her dantian.

However, compared to the relief in her lower body, the pain was bearable.

The Yue Maiden Cultivation Technique was a deep insight from Jiutian Xuannü who encompassed the Nine Worlds.

It was an enlightenment that moderated both Yin and Yang and good and evil.

It gently melted away the Penetrating Power lodged in the pressure points with the True Qi of the Extreme Golden Mean that shouted 'It's possible' for whatever situation.

Just as Qing was forcibly opening her blocked pressure points…

An elderly voice interrupted Qing.

-Hmm, hmm. This old man is called Gaotang Shuang.

Qing was weak against the elderly.

If she could have seen his face, she would have been able to confirm whether he held Evil Karma, but she couldn't do so inside the carriage.

"Oing? Ehh? Suddenly? I'm Ximen Qing."

-This old man wishes to impart teachings to you, so you should properly serve this old man as your teacher.

Why is he suddenly demanding to be served as a teacher?

"I already have a Mast-"

The old voice interrupted Qing and abruptly began reciting a Sutra.

Gaotang Shuang had no choice either.

He was in a situation where if this damn brat refused, he would have to beg her to learn.

So, the plan was to pass on the knowledge quickly before she could refuse and boast about it later.

She was a brat from the Orthodox Faction, so her nature must be different from those of the Demonic Human. As such, perhaps she might return to the Divine Cult later and treat him as her teacher.

Even if she did not, it was probably still better to have her as a disciple than those bastards from the Divine Cult who tried to devour and overcome their own teachers.

-\textit{Dark Sun Earthly Day and Night, as a black sun rises and time where day and night are no different occurs...}

\textit{Ah. He must be the owner of the Demonic Arts.}

Qing kept quiet.

After a brief introduction about seeing a dark sun and getting inspired or whatever, the method of operation for pressure points and True Qi, Movements, and Imagery followed.

The sequence was typical for a Martial Arts Sutra.

Following that, the Martial Arts Window shone brightly.

When opened, it had a Gold Border-

\textit{Huh? Da fok? It's just gold?}

Qing was disappointed.

It was annoying to try out each Movement and perfect the operation as a beginner.

Qing poured out her Free Practice Points and achieved One Star.

At the same time, an uninvited intrusion began in her brain.

The sensation of something kneading and burrowing into her brain was truly indescribable.

"Uegh, ugh, urghhh..."

And when that occurred, it felt like utter fucking shit.

\textit{If it isn't for this kind of experience, where it feels like I might lose my mind, maybe I could have gotten along a bit with Lil Window.}

But after experiencing it, some emotions that could not possibly be regarded as… favorable emerged.

Some kind of evil intent seemed to casually play with her life. A human's life.

And when that happened, she also realized that it was a sort of indifference. One that seemed to say it didn't matter regardless of what happened to her.

\textit{What exactly is it? Is it some kind of god?}

\textit{Aren't the fucking ching chong ling longs supposed to believe in gods like the Jade Emperor or Buddha Baby or some shit? And aren't they supposed to be on the good side?}

\textit{They don't treat people like this, do they?}

\textit{Or is it really just a game?}

\textit{Am I really moving at my will?}

\textit{Why do I always get involved with shit like this, wherever I go and whatever I do?}

\textit{That's right, fucking hell, the Celestial Martial Emperor.}

\textit{There was also something written about that bastard.}

Suddenly, the Strategy Guide she read during installation of the game came to mind.

As if reminiscing while lying in bed, it came back naturally and embarrassingly.

The biggest difference in difficulty levels was the Celestial Martial Emperor.

In easy difficulty, gaining the Legacy of the Celestial Martial Emperor was easy and even those with Unorthodox and Demonic Path tendencies could easily rise to power.

In normal difficulty, the Celestial Martial Emperor was a figure of the past era who was neither Orthodox nor Unorthodox and only pinpointed the Imperial Family. As such, the forces that caused crises were much stronger.

In hard difficulty, the Celestial Martial Emperor was treated as if he never existed, with the government tightly controlling all of Wulin. Furthermore, the level of martial studies in Jianghu had gone to shit, making it difficult to obtain and use advanced martial arts.

Qing chose easy difficulty for her first playthrough.

\textit{Is that why Wulin is like this right now?}

\textit{What if I didn't choose that back then? Would it have been different?}

\textit{What then? What exactly is this world?}

\textit{Uhhh. This ain't good. I need to stop… having bad thoughts… But…}

Qing's body trembled.

\textit{This is so strange.}

\textit{I haven't felt this shit recently, right?}

\textit{Why? Why? Why?}

Then a face came to mind.

Qing immediately recognized why her condition was like this.

That asshole who kept calling himself ‘this being'.

\textit{It's all because of that motherfucker.}

\textit{My face is basically half male half female and my legs are fucking disabled. No shit I'm having a fit, especially after Lil Window started scratching at my brain and even fucked with my mood.}

Surprisingly, she could calm down without any fuss!

But then she also got angry!

Her heart pounded and her hands trembled.

Originally, once a person started to hate someone, they would become a nasty creature that made up reasons to hate even more.

Sure, he might feel it was unjust for all her irrational anger to be directed at just him. But who gave a fuck?

That was why people should always be polite and kind to each other. After all, you never know what kind of shitfest will happen when it comes to people.

Qing's strong emotion caused her to hit the wall of the carriage inadvertently.

It was a move that far surpassed the Peak Realm, embodying an incomparably profound Inner Qi.

It pierced through the inner wall, iron core, and outer wall, shyly revealing Qing's palm outside the carriage.

Gaotang Shuang, who had been reciting the Black Slaying Demonic Palm Sutra for the third time, was shocked by the sight.

Only a single joint at the tip of her elongated fingers was pitch black.

It was evidence that she had properly learned the Black Slaying Demonic Palm.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

About a week had passed.

Qing staggered towards the dining table.

Her right leg was wobbly and her left leg dragged because she couldn't lift it.

Zhi Shengzhu was honestly amazed at her condition.

No matter how many times he saw it, it was always such a wondrous, admirable sight.

To walk on her own despite having faced the Heavenly Reversal Blood Flow Grand Law? It was utter insanity.

Sure, it was more like she was crawling, but Zhi Shengzhu had heard that the Supreme didn't stay his hand, intending to make her paraplegic.

His reasoning was that she had almost completed the Protective Mirror.

The Heavenly Reversal Blood Flow Grand Law was a Sorcery originating from the Blood Cult, renowned as the second most powerful esoteric doctrine of the Blood Cult.

But a martial artist in the Late Stage Peak Realm stood against such a Grand Law of the Supreme?

"Sigh, it's tough. I thought rehabilitation was just some exaggeration. But looks like I'm wrong. It really can be considered a triumph to humans."

Finally, Qing sat down, massaging her thighs and making a fuss.

Then she grabbed chopsticks and began to wield them quickly.

Food needs to be eaten.

Why? Because it's right in front of her. Duh.

Zhi Shengzhu intently watched Qing wolf down the food.

To an onlooker, it might seem like she had a vendetta against the food.

However, Zhi Shengzhu was watching not that vengeful spirit of a glutton but her hand.

All of her long fingers were pitch black.

This signified that the Black Slaying Demonic Palm had reached Three Stars.

It had only been a week since the Sutra was passed on.

\textit{A single week? A single week was all it took to achieve Three Stars?}

Zhi Shengzhu had barely stepped into the Second-Rate Realm.

He had used his intellect to earn him the role of Secret Pavilion Leader among the Divine Cult disciples.

But even his sharp mind could not comprehend the unprecedented speed at which Qing mastered the Black Slaying Demonic Palm.

If it was an Inner Qi Cultivation Technique, reaching the Grand Star directly due to its familiarity could at least be understood.

But the Black Slaying Demonic Palm was a Palm Technique which focused on long-range strikes.

\textit{How could a sword user suddenly excel in Palm Techniques?}

\textit{Was there some inherent talent in Palm Techniques that she herself was unaware of?}

Zhi Shengzhu didn't know that Qing had also mastered the Buddha's Palm and the White Hand Demonic Arts.

The Buddha's Palm was among the most revered Divine Arts when it came to Palm Techniques and the White Hand Demonic Arts was the roots of many branches of Demonic Arts.

Since the mysterious principle of the Black Slaying Demonic Palm belonged to Palm Techniques, it was essentially akin to the Buddha's Palm.

Moreover, the Penetrating Power of the Black Slaying Demonic Palm was originally modeled after the White Hand Demonic Arts.

Thus, the operation and movements were natural to her as if she already knew them, not requiring any more Practice Points to be invested for understanding.

Qing emptied her plate and leaned back in her chair, before calling out to Zhi Shengzhu.

"Hey, kiddo."

"Damn it. Kiddo, my foot."

\textit{Please, speak.}

\textit{Shoot. The words came out wrong.}

Zhi Shengzhu realized his mistake.

But unfortunately for him…

Qing just had to have heard him, thus flashing a teasing smile.

"You always look unbothered, but it seems like you're actually concerned about your height, huh?"

"I have a disease where I sometimes speak nonsense."

"Sure. Whatever you say, kiddo. From what I see, it's because you don't eat enough. You need to eat more to grow."

Zhi Shengzhu's eyebrows twitched.

\textit{I didn't eat enough? Whose fault is that!}

The dining table in Zhongyuan was designed to rotate, making it easier to serve oneself.

Whenever Qing wanted to eat something, she would turn the dining table and make sure all the dishes were right in front of her.

As such, Zhi Shengzhu was always hindered when trying to eat.

"You must be very glad that you are tall, Young Lady."

It was a remark of ridicule.

After all, in Zhongyuan, tall women were not popular.

However, it had no effect on Qing.

"Well, of course. I'm sure our little kiddo over here would know if he was a bit taller. Do you even realize how fresh the air is up here? Every time I sit down, the air down there is so filthy I can barely breathe, you feel?"

"……."

"But then again, when we sit, our eye levels match, don't they? Where does this difference come from? Is it the legs? Or is it the legs?"

"...Bullshit."

\textit{Bullshit.}

For once, Zhi Shengzhu's outward expression and inner thoughts aligned.