\chapter{Who Would Threaten With A Sword… (2)}

And the strict law established by Qing was that the victor must duly pay respects to the vanquished.

It was the noble act of accepting the will and the remaining belongings of the defeated.

Thus, Qing did just that.

But…

\textit{There was…no moneybag?}

\textit{...Wait a fat fucking minute, how could this be real!}

Qing was infuriated.

This was a serious betrayal.

Fine, the villain had willingly offered her back to be stabbed. But still, why was there no reward for the good deed she so painstakingly performed?

This reality should not exist.

Just to be sure, Qing conducted a thorough body search once again.

During this, something was felt in her hand.

It was something sewn inside the undergarment.

The hard, rolled up item was not a moneybag.

However, if it was hidden this well, it must surely be something valuable.

\textit{That's right, this is the shit! I always believed that you would deliver!}

Qing tore open the undergarment with a bright expression.

And the moment something was grasped in her hand—

Suddenly, the Martial Arts Window insisted on being opened.

According to Qing's experience, this was what happened when a complete Secret Manual or a Sutra was touched.

Qing opened the Martial Arts Window.

A newly added, sparkling martial art caught Qing's eye.

Blissful Maiden Arts. The Border was golden.

\textit{Gold, is it? Gold is right below Purple.}

\textit{And it's also an Inner Qi Cultivation Technique, huh?}

\textit{The more Inner Arts, the better, I guess.}

\textit{I should briefly return right now and ask Master if this martial art is fine to learn.}

That's right.

It seems Qing, too, has grown!

But before that…

Qing remembered Ximen Surin's beseeching.

'As Disciple often comes into contact with martial arts, heed my advice. Memorize the Secret Manual completely before burning it and just burn the evil ones immediately.'

What she implied was that a Secret Manual merely being possessed could sprout seeds of discord.

And honestly, any discord was now incredibly tiresome, even for her.

Qing took out a flame stick.

A flame stick was a tube designed to hold a tinderbox.

Though a fairly valuable item, it was something Ximen Surin had prepared for her fragile disciple who couldn't yet produce True Fire of Samadhi.

For reference, the True Fire of Samadhi was a technique used by martial artists at the Transcendent Realm to intensify heat into a singular point using the principle of Force Compression.

Brutally thrusting in True Qi to merely light a tinderbox was trivial, but it was an arts already acknowledged for its convenience long ago.

Of course, since Qing was still at the Peak Realm, it was just a matter of holding a flame stick to light a fire. There was nothing spectacular to it.

A few handfuls of dry leaves gathered in the spring were enough to catch fire in the flame stick.

The Secret Manual of the Blissful Maiden Arts was a bamboo strip soaked in oil, but in the end, it was nothing more than wood.

How long could it possibly last?

The Secret Manual of the Blissful Maiden Arts burned.

The esoteric doctrine passed down only by the Palace Leaders of Bliss Palace blazed fiercely.

Next to it lay the body of one such Palace Leader.

It was the moment the lineage of an esoteric doctrine, long cherished by a certain sect, was severed.

Qing looked around once and then continued on her way.

She didn't know what that villain intended to do..

But regardless, she was a bitch who had accumulated over four hundred Evil Karma.

Wouldn't it just be a trap at most?

It's better to not get entangled and end up in a situation like the one in Dongting Lake.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"...So."

Zhi Shengzhu summarized the report with an expressionless face.

"Ximen Qing ambushed and killed the Bliss Palace Leader, then burned the Secret Manual before heading towards the Divine Maiden Sect?"

"Yes. I saw it clearly with my own two eyes."

An assassin from the Demonic Cult Outer Hall's Covert Operations Division answered.

He was one of those sent to assist Xian Yue in luring the target.

To the assassin, Qing seemed as skilled as any expert in his industry.

A killing intent that didn't leak for even a second, a single clean move without an ounce of hesitation.

Even a Master who had reached the Late-Stage Transcendent Realm couldn't react and was killed instantly. As such, if she had been an assassin, she would have made her name known in Zhongyuan long ago.

It wasn't something that could be done without a substantially venomous heart.

"And she didn't even look at the Secret Manual?"

"It seems she has no interest in a Demonic Human's Secret Manual."

"She turned out to be even more ruthless than expected. Truly a disciple of Ximen Surin."

Zhi Shengzhu clicked his tongue.

Ximen Surin's hatred for Sex Fiends was well known.

So much so that there was no distinction between male and female Sex Fiends.

Male Sex Fiends were trash that should not exist. Female Sex Fiends were trash that brought shame to all women. And with the claim that all trash should be burned, she torched the corpses she killed. 

Or so it was said.

Of course, Zhi Shengzhu, who was only fifteen, had not yet experienced the old Masters who were active in previous generations.

However, even from the records that remained, he knew that Ximen Surin was an absolutely insane slaughterer.

He had thought she had become more peaceful after she had stopped appearing in Jianghu and had secluded herself in the Divine Maiden Sect.

But apparently not. It appeared she had passed all her hatred onto her disciple.

But well, it made sense. After all, how else could that disciple recognize and deal with an old monster who had tucked herself away for many years in a remote corner of Zhongyuan? Ximen Surin must have told her disciple about Xian Yue.

"A female expert of the Orthodox Faction with a venomous heart... This truly complicates things. Does that mean Fushen-di has once again made its way to such a person?"

It was estimated that it would take at least forty years for Fushen-di to completely shake off the traces after being marked with its owner's Inner Art.

And even that was the minimum estimated time.

The key just had to have ended up in the hands of an Orthodox Faction martial artist right before the completion of the great mission.

"What should we do?"

"I will take direct command. Mobilize all cult members to secure Ximen Qing. Before Ximen Surin notices."

The assassin swallowed hard.

Could it be that he could actually witness a display of such exquisite command?

Zhi Shengzhu's martial arts prowess was just at the threshold of the Second-Rate Realm.

However, the true value of the Demonic Brain did not lie in martial arts prowess.

A Net of Heaven and Earth directed by the Demonic Brain himself...

"Pavilion Leader! I will report!"

At that moment, another assassin entered and shouted.

Zhi Shengzhu looked at the second assassin with an expressionless face. But for some reason, its blankness seemed reproachful.

"If you are here too, then who is tracking the target?"

The second assassin answered.

"The Supreme has captured her personally."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"You there. Heed me."

The voice was casual, as if there was nothing out of the ordinary.

Meanwhile, Qing was startled and turned her head.

It was an impressive man with long hair reaching down to his waist.

With a face that looked stubborn due to the jaw set in determination, he was grinning slightly at Qing.

Qing's expression hardened.

Qing was a Master.

It was not easy to deceive the eyes and ears of a Master.

But she wasn't able to notice someone who was this close.

Clearly, it was an incredibly abnormal situation.

Qing quickly checked the opponent's Karma.

-998.

Qing immediately regretted it.

\textit{Fuck me sideways. I shouldn't have checked.}

\textit{If things go to shit, I might be the one to complete his thousand.}

Qing was fundamentally strong against the wicked and weak against the righteous.

But at the same time, she was also strong against the weak and weak against the strong.

Weak villains were like fun toys, but when she met a strong villain, she shrank back instantly.

After all, it would feel so unfair to die now.

She had barely managed to survive after rummaging through trash cans, eating rotten food, and using insects as a side dish.

And just when she thought she might finally start to fit into this world or perhaps even have affection for it...

For now, Qing tried to initiate a conversation.

"Who are you?"

"This being?"

\textit{Ah shit.}

Qing's expression soured.

\textit{A bastard who calls himself ‘this being'?}

\textit{This motherfucker must be batshit crazy. There's no doubt that he's nuttier than a peanut.}

"If this being must say, a creditor perhaps. Since you have this being's property."

"I do?"

"Yes. A flute about this long. Have you seen it?"

The man spread his arms.

It was quite a familiar length.

Qing glanced at the man for a moment, trying to gauge him.

Despite clearly being in her field of vision, something about him was blurry, hardly seeming human.

So, he was either not human or an extraordinary Master.

Qing made up her mind quickly.

"Ahaha. I found it on the road. Didn't know it had an owner, huh. Do I just need to return it?"

It was better not to antagonize him.

Qing promptly took out Fushen-di and offered it.

The man grinned widely.

"Very good. A thieving cat who knows her duty, it seems."

Goosebumps rose all over Qing's arm.

\textit{Thieving cat?}

\textit{Did he really just say thieving cat\footnote{'thieving cat' is more commmonly used to refer to woman having affair with married man}? With his own fucking mouth?}

\textit{Can a person even say something like that while completely sober?}

There was absolutely no doubt that he was a complete lunatic.

Qing decided once again.

\textit{I better not get involved.}

Just as Qing resolved as such, the man asked.

"But. Have you blown it?"

She had definitely heard that it was some magic flute that only went ‘Open Sesame' after one made a sound with it. Basically, it was locked for anyone else.

\textit{Is it worth lyings? Would he even fall for it?}

\textit{What if I get stabbed in the guts for lying?}

Qing's pupils flickered sporadically, uncertain of what to do.

Then the man chuckled.

"You blew it?"

"...What if I did?"

"What else can be done? Not only did you take this being's property without permission, but you also became its owner. As such, there is no choice other than for you, too, to become this being's property."

\textit{How in the ever living fuck can each of his lines be so cringe? Hell, just hearing it makes me feel like shit.}

Qing took a deep breath.

Then, she exhaled deeply again to calm herself down.

"I apologize for asking upon our first meeting, but could you perhaps tell me what realm you are in…?"

"This being? An existence who will soon reach the Natural Realm."

The Natural Realm was a legendary level believed to have been reached by the Sword Emperor in his later years.

But according to Ximen Surin, no one in the world had actually reached it, so it was just a lie made up by people.

Yet, here was an existence claiming to be on the verge of reaching the Natural Realm.

Then, does that mean he's just below it?

"Ah. Are you at the Celestial Realm then?"

"No. This being will reach the Celestial Realm soon too."

"Then you're in the Life and Death Realm...?"

"No. This being will reach the Life and Death Realm soon as well."

\textit{What kind of dogshit is this? Why the fuck is he shitting out of his mouth instead of his asshole?}

Qing barely managed to hold back from swearing five hundred times.

\textit{Let's not use any bad words.}

\textit{I can't trigger him, after all.}

"So you mean you're in the Profound Realm?"

"If this being truly set his mind to it, he could reach the Profound Realm by tomorrow."

\textit{So, he isn't in the Profound Realm either.}

\textit{Why does it feel like it keeps going lower and lower?}

Qing harbored a glimmer of hope.

After all, she might stand a chance up to the Transcendent Realm.

\textit{Motherfucker acted like he was him. But seems it ain't the case, huh.}

\textit{You better brace yourself for a beating of five hundred Buddha's Palms.}

Qing continued to question.

"Then, the Unrestrained Realm...?"

Instead of answering, the man simply snapped his fingers.

Qing's face became tinged with disappointment.

\textit{Fuck! So close!}

\textit{Just a little more would have been perfect… Why stop there?}
