\chapter{Who Would Threaten With A Sword… (8)}

Thus, a mountain of poppies flew into the carriage and tumbled onto the soft blankets.

Qing was honestly a bit surprised.

\textit{Did that blatant tantrum really work?}

\textit{Even though I spoke as if reading off lines from a textbook?}

\textit{What the fuck? Do people in Zhongyuan tend to believe this kind of acting?}

Of course, they did not.

However, there was someone who pretended to be fooled by the obvious act.

'It seemed really fake, but just in case… Just in case it was genuine… What if it actually hurts?'

Parents' grace, children's filial piety, beloved lovers, and irreplaceable friends could indeed think that way.

But there was no way the Demonic Adept outside would be.

And if anything, they might have planned to control her by making her addicted.

Ah! So that was what they were trying to do.

However, there was no shot she would get fooled.

Qing didn't indiscriminately suck on the poppy.

No matter how much she knew she wouldn't get addicted or that it wasn't harmful to her body, it was still a drug.

There was a psychological resistance to it.

And then, the desert appeared.

Qing, who had never seen the grandeur of the desert with her own eyes, was overwhelmed with emotion.

And within less than an hour, she realized that the daytime desert was really annoying.

However, the nighttime desert was mysterious and beautiful, thus making Qing's magnificent chest filled with emotion once again.

The reason for this was because Qing had a strong resistance to cold.

But the heat was a bit too much.

Especially being buried under blankets in a carriage with no ventilation.

She couldn't tell if they were transporting her or making a steamed Ximen Qing.

As she was panting like a dog in the midday heat, bundles caught Qing's eye.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tianshan.

Also known as the Mountains of Heaven, the name alone suggested a majestic mountain range, the end as well as the ceiling of Zhongyuan.

The highest peak was Victory Peak, about three times the height of Changbai Mountain.

Additionally, there were countless peaks twice the height of Changbai Mountain, revealing a stunning scenery with white eternal snow in the middle of the mountain range.

On the other hand, it was also unsuitable for human habitation.

Barren land, rugged terrain, and perpetually cold nights.

There weren't even many animals, so farming and hunting were not options.

This desolate land was where the Heavenly Demon Divine Cult had settled.

This was why the Heavenly Demon Divine Cult had invaded Zhongyuan four times.

Living in such a harsh and bleak land naturally fueled hatred towards Zhongyuan.

Conversely, it was also why the Demonic Cult remained.

It was hidden deep inside the mountains at the end of the world, past the plateau and desert, taking three months of continuous travel.

No matter how much the bastards at the Demonic Cult were hated and resented, no one would endure such a distant expedition to chase them.

The desolation of the grasslands and the alternating freezing and thawing of the desert day and night would wear them down until they finally saw the distant snowy barrier.

By the way, why did it never seem to get any closer?

The height of the Tian Shan ignored all sense of perspective.

Upon seeing it, even the fiery desire for revenge would die down and people would think, ‘Ah, this isn't worth it'.

Indeed, revenge was an empty endeavor, so they might as well forget everything and enjoy delicious food by the warm fire in a cozy home.

The prisoner transport journey was about 9000 li\footnote{Ancient Chinese of length. In this novel's setting, Ming dynasty, 1 li is about 300 meters}, taking three months.

In modern terms, it was 3,600 kilometers, which was why no one pursued the Demon Cult, even though its location was openly known.

Prisoner transport was inherently not an easy task.

The criminals of the Divine Cult were often those who had fled from the Divine Cult.

And the members of the Divine Cult included those who had committed crimes in Zhongyuan and fled.

So, the prisoners of the Divine Cult were those who had fled, committed more crimes, and fled again.

This meant they were twice as formidable as typical escapees.

However, there had never been a prisoner transport as large and as damaging as this one.

The warriors of the Divine Cult who participated in the transport boasted of their heroic feats.

As boasts often go, there was a bit of exaggeration, of course.

Apparently, this prisoner is so crazy that she enjoys smashing people's heads just by making eye contact.

And hundreds of assassins from the Outer Hall's Covert Operations Division died, so they had to call in all the Peak Realm Masters.

It must have been so very difficult having such a prisoner in tow when it was hard enough just to travel the path.

Those who heard this were ready to give words of praise. However, upon seeing her, they responded in a different manner.

"...So, that is?"

A girl, held by the Purple Lightning Demonic Warlord, was smiling and waving.

At first glance, her actions seemed frivolous, but they actually exuded elegance.

For a frivolous action not to seem frivolous, one must have ingrained habits from long training in a rather noble family.

She must be the lady of some prestigious family. She just had to be.

"...She was the one who went around smashing heads apart?"

"Don't be fooled. It's all an act."

"I'd like to say you worked hard and did a good job. But hey, come on now. That's a bit much. Even lies should have limits. How can everything you said be a lie?"

The same conversation was happening everywhere.

With that, Qing managed to fool them until the very end.

Some were able to guess from the sad expression of the Purple Lightning Demonic Warlord, who was flickering with Purple Lightning Qi.

That prisoner must be heavily drugged.

The Purple Lightning Demonic Warlord's daughter was notorious for her bad temper.

Near the end of her life, she became famous for being an incorrigible drug addict.

As such, his reaction made sense. After all, this was Cui Liweng, who failed miserably at raising his daughter.

After that.

Qing was handed over to the women.

She couldn't be presented to the Supreme in such a dirty state.

The women washed, scrubbed, and polished Qing.

To be honest, it was a process that was quite humiliating for Qing.

Even though she was all grown up, she had to helplessly submit to being treated like a doll by many women.

However, fortunately, she was under the influence of drugs, so she passed through it without much resistance.

Rather than humiliation, she even somewhat enjoyed it.

And if the drug's effect hadn't worn off at the end, she might have continued to enjoy it.

With that, Ximen Qing added a huge dark chapter in her life.

That night.

Ximen Qing met the Alleged Supreme again.

A throne placed between red and blue silk, hanging from a high platform like an altar.

It looked more like an altar than a grand hall.

Which made sense. Because it was indeed an altar.

The Heavenly Demon Divine Cult were the descendants of a pseudo-religious group.

They had later degenerated into the avengers of hell, but they still maintained some of their traditions.

On the right of the Alleged Supreme was Zhi Shengzhu, who arrogantly crossed his legs and looked down at Qing, sitting on a more modest chair.

\textit{What's up with that fucker? He was actually the second-in-command?}

Qing felt both regret that she hadn't killed him and relief that she hadn't acted impulsively and jeopardized her safety.

As a result, the conclusion she had to make was clear.

She would kill him before dipping.

Meanwhile, dozens of Masters were lined up in two rows inside the grand hall.

The Alleged Supreme, looking down at Qing who stood on her two legs, spoke.

"You killed many cult members on your way here?"

Not wanting to be beaten again, Qing put on a servile smile.

"About that..."

"No. It is fine. It is not particularly blameworthy. It is their fault for being weak and dying anyway."

"Hehe."

She could endure this as much as she needed. The humiliation of barely ekeing out a smile.

Fine. I shall be hit by the drizzle.

But the storm is mine.

Qing recalled a famous line from a certain creator who was worshiped as a god.

If only that narrator hadn't collapsed from being hit by too much drizzle; he would have left a great mark on modern cultural history.

\textit{Welp. Too bad, too sad.}

"But you know. hmm."

The Alleged Supreme chuckled.

"This being thought you were completely broken after the beating. But it seems that is not the case, huh? You must be cursing this being as a bastard while wagging your tail like a bitch, aren't you?"

"Hehe. I don't know what you're talking about."

"Is that so? How so very strange. Hm, Yunhua."

The Alleged Supreme snapped his fingers.

A woman appeared gracefully through the silk curtains.

Even Qing, who had trained her aesthetic sense with the Jade Qilin, recognized her as a top-notch beauty.

"Supreme. Did you call for this girl?"

"Strip."

"Yes."

The woman immediately pulled off her palace attire.

The Alleged Supreme gestured at her.

"Look, do you see this?"

Qing frowned.

\textit{What is this? Ostentation? Is he tryna flex?}

"This place is filled with men. Yet, she strips. Because a woman who does not even know shame strips when told to. What a stupid bitch."

The woman's face turned pale and her hands trembled.

Qing felt sorry for her.

\textit{What the hell? He's the one who told her to strip, but now he's making a huge Wahhh over it. The fuck is wrong with him?}

But then, Qing checked the woman's Evil Karma.

\textit{Mmm. Nevermind. I guess she can get shit on a bit more.}

"This is why women are so boring. All they know is how to act coy."

The woman's trembling intensified.

"But this being hates it when anyone dares to defy him. You experienced that, didn't you?"

Qing's smile deepened.

\textit{This motherfucker. I'm gonna burn him alive.}

If you make a bonfire for someone, they'll stay warm for a while.

But if you set fire to their body?

They'll stay warm for the rest of their life.

She intended to give him that very lifetime of warmth.

After all, only by embracing him with such heat can that cheeky son of a bitch be taught some fucking manners.

"Yes! That is it! Obedient on the outside, yet secretly harboring killing intent on the inside. This being thought that you were just like the other bitches. But it seems not. Ha. It is making this being excited. However."

Goosebumps ran up Qing's arm and reached her neck in an instant.

\textit{What did this crazy motherfucker just say?}

"Take her to the Bliss Palace and make her learn every single Fairy Arts there. If that does not work, feed her elixirs until she reaches the Transcendent Realm. Overhaul Rebirth is perfect for enhancing beauty, after all."

\textit{New martial arts! Elixirs!}

Qing's eyes gleamed.

\textit{Fuck Demonic Arts and whatever. I have to fuck him up.}

\textit{This motherfucker is a creature that should not exist in this world.}

To put it nicely, it could be called a rather revolutionary thought against a harsh oppressor.

\textit{This Natural Realm wannabe motherfucker, who's barely at the Unrestrained Realm, is just asking for it, ain't he? Does he want to die that fucking badly?}

Qing (Late Stage Peak Realm) thought as such.

\textit{Just you wait until I reach the Transcendent Realm.}

\textit{I'll fuck you up with the Buddha's Palm five thousand times.}

Qing swallowed down her anger.

At that moment. Zhi Shengzhu tried to dissuade the Alleged Supreme.

"Supreme. She is a serpent-like bitch. She will surely bring great harm to the Divine Cult. Please reconsider."

"Enough. This being has already decided."

"...I shall obey the Supreme's command."

Zhi Shengzhu bowed his head.