\chapter{Who Would Threaten With A Sword… (3)}

"So, what are you going to do now? Will you refuse an elder's cup? Then, you shall have to chug the penalty drink, you see?"

"……?"

\textit{The fuck was he yapping about? A cup? A penalty drink?}

\textit{Alcohol? Is it alcohol? Like, penalty alcohol? A drinking game?}

It was an expression not commonly used in Wulin today.

If used now, one might get ridiculed for having the stench of a boomer.

'Did you perhaps live during the era of the Celestial Martial Emperor?' was what people would ask.

Qing blinked her eyes.

It was an expression that anyone could recognize.

The man burst out laughing.

"Will you follow without a fuss?"

"Can't I just stay here without a fuss?"

"If not, you'll have to take a beating."

\textit{Motherfucker, this piece of shit who can't even compare to my Master is tryna fuck with me, huh?}

However, Qing was not Ximen Surin.

She was merely a Late Stage Peak Realm martial artist.

Common in every city's martial halls, just one of many good fighters living harmoniously.

\textit{It's seriously so frustrating living at the Peak Realm.}

\textit{But the Transcendent Realm is still out of reach.}

\textit{And maybe something got fucked, seeing how a Mission for the Transcendent Realm isn't coming up.}

\textit{Is it because I met the final boss first?}

\textit{If it's not that, I'll have to reach the Transcendent Realm using the process that everyone else goes through, but I don't even know where to start with that.}

"Then, is there a possibility to come back if I follow you?"

"This being promises on his name."

Qing's eyes narrowed.

\textit{How the fuck am I supposed to trust the words of a bastard who is gonna reach one thousand points soon?}

Qing asked again for confirmation.

"You're not trying to trick me, right? Like, you're telling the truth, but in reality, I come back dead or disabled or something."

"Ha. Are you saying right now… That this being would stoop to such petty tricks? You dare? Even after this being swore on his esteemed name?"

"No, it's not that I doubt you, it's ju-Ugh."

Suddenly, the man was right in front of her.

Qing was startled.

The man's fist had deeply penetrated, almost to his forearm, in Qing's abdomen.

Qing flew back, bent at the waist.

A dizzying flight ended by crashing into a tree.

Qing gripped her stomach and rolled on the ground.

"Kkuhuk, keuk. Kkeheuk…!"

\textit{I-I can't b-breathe…}

Qing desperately gasped for air.

But her crushed lungs refused to expand in her tightly constricted chest.

Her head was filled with pain.

She felt like she was suffocating.

\textit{It hurts. It hurts so much. My stomach...!}

It seemed as if a blade was flowing through the pressure points.

A sharp blade forcibly ripped, tore, and bit through the narrow blood vessels.

Nothing, except pain. Agh.

Thought itself stopped due to excruciating agony.

She felt dizzy.

From the horizontally lying ground, two pillars stuck close to her.

They were two feet right next to her sides.

And one of the legs had moved far away.

\textit{No fucking shot.}

Qing tried to cover her head.

But it was already too late.

The man kicked Qing's head right then.

Thwack. The world shook before seeming to turn off.

Qing's body went into the air again.

Then, she regained consciousness from the impact of her fall.

All she could see was a reddish aura in her field of vision.

Blood had filled one eye because a blood vessel had burst.

Qing had no chance to react.

A strong force grabbed her hair and yanked.

Her face felt like it had shattered.

The enemy's Penetrating Power was still tearing through her insides.

The world was red.

And her scalp relentlessly burst in pain, as if continuously telling her it was ripping apart.

The man's voice burrowed into the spasming Qing's ears.

It was practically drenched with pleasure and joy.

"Protective Mirror? For just a Peak Realm nobody, you handle it quite adeptly, don't you? This being was thinking of bursting at least one eye."

"Why, why?"

"To play a flute, all you need is your mouth and hands."

Qing clenched her teeth.

She was a child being watched over by the lonely star of Heavenly Slaughter.

The pain soon turned malignant, seeping into the bones.

\textit{This fucker, I won't let you off easy.}

\textit{Motherfucker. You're going to die. In the worst fucking way. I'll make sure of it.}

Whether Qing had the right to be angry was not important.

After all, Qing had always picked out only the bad guys before toying with them.

Her Righteous Karma had just exceeded one thousand four hundred and fifty points.

Soon, she would be able to exchange one thousand five hundred points, so Qing, in fact, prided herself as the nicest person in all under the heavens.

This feeling of incompetence fueled her anger.

Thus, helplessness and anger pressed some deep-seated power button.

\textit{The fuck is up with him? Does this fucker have anger management issues?}

\textit{Cowardly hitting first when we were having a perfectly good conversation?}

\textit{On top of that, he's more of a Master than me.}

\textit{Pathetic motherfucker. Piece of shit. Just you wait. You wanna play dirty? I'll show you what it means to truly play dirty.}

Contrary to her inner thoughts, Qing smiled.

Her face, swollen on one side, bore an expression of utmost servility.

"Hehe, you could have just used your words…"

It was the dread inherent in a bearer of Heavenly Slaughtering Star.

Because she was not just an existence that craved blood and pain without reason, but a monster that knew exactly when to strike.

If the man wanted to become old in peace, he should have killed Qing right then and there.

But who would think that a Female Expert of the Orthodox Faction was born with Heavenly Slaughter?

The man gave a satisfied smile.

"Indeed, as expected. Female brats must be beaten for them to listen."

\textit{Did he live in some ancient times? The fuck is up with this boomer?}

\textit{Shit, I should just rip off his mouth.}

\textit{Come to think of it, this is primitive, uncivilized, ancient China, so it obviously makes sense that this fucker is an uncivilized piece of shit as well.}

Qing kept smiling like a fool.

"Hehe, if I listen well, there's no need for a beating, right?"

Upon hearing this, the man looked rather disappointed.

"Were you not supposed to be an unbending female expert of the Orthodox Faction? This being thought you might be a bit interesting, but in the end, you are nothing more than a mere brat. Tsk. No matter. Take her away."

The young man tossed Qing aside and then turned his body.

Afterwards, figures in black appeared from all sides and bowed respectfully towards his back.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The state of Qing, who was dragged here, was a mess.

Half of her face was swollen, her eyes squished and filled with blood, completely red.

Her new martial attire was all dirtied from rolling on the ground, so it was natural for Zhi Shengzhu to click his tongue.

"Tsk."

Though she had a servile smile, Zhi Shengzhu sensed that the girl in front of him was cut from the same cloth as him.

A person whose inside and outside were completely different.

It was the sharp intuition of one who met his own kind.

According to the situation, it was one where cooperation needed to be sought calmly.

After all, wouldn't it be considered a relief if there were at least no interference, even as she ground her teeth?

If only that old monster Xian Yue had not failed.

Zhi Shengzhu suppressed his frustrations.

He couldn't dare blame the Supreme, after all.

Given that it had already come to this, he thought he might as well throw a carrot.

"Do not hold too much ill will and animosity. After all, haven't you also done us wrong?"

Upon hearing this, Qing answered with a smile.

"Hello? Kiddo. You should greet someone when you first see them, shouldn't you? I'm Ximen Qing! Who might this little guy be? Ah. Are you a Master too? You don't happen to have some mental illness that makes you punch people in the middle of a conversation, do you?"

Her smiling face and words were fierce.

\textit{Wasn't she trying to hide her inner thoughts? Did I get it wrong?}

Despite such doubts, Zhi Shengzhu remained expressionless.

"I am Zhi Shengzhu. Though I lack much, I am the Secret Pavilion Leader of the Divine Cult."

"Secret Pavilion Leader? Is that a high position?"

Qing looked down at the small boy with a grin.

\textit{To think they kidnapped me in broad daylight and the first place they drag me to is in front of this kiddo.}

\textit{Is he some important figure?}

\textit{Would it make that bastard angry if I killed him?}

\textit{For now, I should keep this in mind.}

\textit{After all, that bastard is still around here somewhere.}

Qing looked at the expressionless Zhi Shengzhu and thought as such.

She didn't feel the need to check the numbers above his head anymore.

After all, in order to survive, she first needed to sort out this deep rage pulsing in rhythm with her heartbeat.

"It is regrettable to have to meet under these circumstances, but we have our own reasons too."

"Well, who doesn't have their circumstances? Well then. Let's try hearing your side of the story."

"Now is not a good time to explain."

Zhi Shengzhu pushed forward a bowl that was on the table.

"The pain must be severe. This should help you feel better."

"What's this?"

"It is a dream soul medicine made by mixing wild nectar and poppy extract. If you drink it and sleep a bit longer, you shall feel much better."

Wild nectar signified honey and dream soul medicine was a kind of sleeping pill.

Basically, he was saying it was honey water that had drugs and sleep medicine.

It might sound crazy to drink such a thing, but in Zhongyuan, poppy extract was considered a panacea effective for pain relief and reducing fever.

As such, it wasn't a herb mixed with malicious intent.

"Is that so? Well then, out of courtesy."

Qing drank the honey water refreshingly.

The warm, sweet honey entering her stomach seemed to ease her mood a bit.

After all, opium poppy was harmless to her body anyway and she knew from multiple experiences that dream soul medicine wouldn't work on her.

At times like this, it was rather a shame her Constitution was the way that it was.

One side of her face still pulsed painfully with each heartbeat.

It would have been nice if I could pass out after taking some sleep medicine.

Afterwards, Qing obediently boarded the carriage.

The windows were merely thick paper stuck to iron grates, poorly letting light seep through.

Once she climbed inside, the sound of a lock clicking shut came from outside.

The carriage, designed as a type of sleeping chamber, was quite cozy.

The light seeping through the thick paper was not bothersome, and her feet sunk into several layers of quilted blankets, reaching to her ankles.

Qing laid down in the spacious carriage.

The carriage seemed to start moving with a slight jostle, but no distinct vibration was transmitted.

Soon after, the effects of the poppy extract kicked in and the pain in her face gently subsided.

As she lay buried in the bedding, she felt as if she were floating.

With that, Qing racked her brain for the first time in a while.

\textit{Aside from the son of a bitch who kept yapping about how he would soon reach the Natural Realm, the treatment wasn't bad at all.}

\textit{Actually, it was quite polite.}

Qing recalled Fushen-di that had been taken away from her.

The ones looking for that flute were from the Demonic Cult and that little kid had blabbered something about the Divine Cult, so now she clearly understood their identities.

\textit{Also, they need something from the flute, but because of the Blow to Unlock function, they evidently need me, the owner, as well.}

\textit{Sons of bitches. Let's see if I ever listen to them.}

Qing had no intention of heeding the requests of such bad people in the first place, muttering to herself indignantly.

In fact, the Demonic Cult had only garnered resentment, so they were far too rotten of a group to seek cooperation from in the first place.

But the point that they had earned her enmity was important.

Once she bore a grudge, Qing was the type to relentlessly retaliate.

After all, hadn't she never backed down even against the final boss who had reached an unknown yet formidable realm?

\textit{A fucker in the mere Unrestrained Realm dares…}

\textit{Demonic Cult? Motherfuckers, just wait and see what I do to all of you.}

A sinister starlight leaked from Qing's eyes, casting a red glow in the pitch-dark interior of the carriage.