\chapter{Who Would Threaten With A Sword… (4)}

The prisoner transport carriage of the Heavenly Demon Divine Cult was a masterpiece of the Weapon Pavilion affiliated to the Inner Hall.

It had reinforced steel grids for durability and weight, and the use of modular parts made maintenance convenient.

It could also obscure the prisoners' sense of time through lighting control and inject various types of poison gas through two stokeholes below.

And it had a comfortable ride.

Not exactly to protect prisoners' rights, but a mechanism to ensure that prisoners sedated with drugs did not wake up.

So when there was a thumping noise on the carriage, the assassin from the Outer Hall's Covert Operations Division, who was fanning the Qi Dispersion Poison Incense in the stokehole, was inevitably startled.

\textit{How could she be awake already?}

\textit{Was there not enough Dream Soul Medicine?}

\textit{I used three times the usual dose, though?}

The only thing audible, due to the high soundproofing, was the thumping noise against the wall.

The assassin pushed aside one wall panel and spoke.

"What is the matter?"

-Ah. Ah. You can hear me, right? I'm bored. Give me a snack.

She spoke as if snacks had been promised to her. Like it was some god-given right. The flabbergasted assassin was momentarily at a loss for words.

-Hurry up. I'm getting dizzy. Give me snacks. Snacks!

"Look here, your current situation is-"

-I don't care about that. Snacks are more important. If you kidnap someone, you should at least provide meals and snacks, right? Isn't that basic etiquette?

"No, what the..."

The assassin was at a loss for words.

Instead, he scooped out his pocket and dumped it into the stokehole incense burner.

It was the powdered Dream Soul Medicine.

He then increased the fanning speed, causing thick smoke to billow into the carriage.

The effect was immediate.

The girl's voice rose in pitch.

-No, who asked for incense to be burned!? I said to gimme snacks! Hey!

"W-Wait a moment."

-Hmph. You should have listened to me earlier.

The assassin hurried towards the lead carriage.

Having reached the lead carriage, he reported to the Secret Pavilion Leader.

"Pavilion Leader, Ximen Qing is asking for snacks. What should we do?"

Zhi Shengzhu looked at the assassin expressionlessly.

"Didn't she inhale a lot of Dream Soul Medicine?"

"She seems to have a Constitution that makes it ineffective."

There were individuals whom Dream Soul Medicine did not work on.

Such people weren't even all that rare.

After all, Dream Soul Medicine itself wasn't very toxic.

"Should we use a different drug?"

Other drugs were too potent.

If her brain were damaged, she couldn't be interrogated.

Zhi Shengzhu thought for a moment then shook his head.

"For now, accommodate her. Give her what she wants. No, actually. I'll go there myself."

Zhi Shengzhu recalled a trait common in humans.

When people were uneasy and dizzy, they unconsciously cherished those nearby.

It was like hostages who developed feelings for their captors.

Even if not to that extent, if it could slightly reduce psychological distance, it might later facilitate smoother cooperation.

That was Zhi Shengzhu's ulterior motive.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{My legs are cramping.}

\textit{As soon as the poppy run out, they started acting the fuck up.}

Leg cramps were a vicious pain.

It incessantly bothered one while they were awake, tingling and feeling utterly unpleasant.

It would have been better if she could have walked around, but even though the carriage was large and spacious, it wasn't nearly the size where she could take such actions.

"Hey. What have you done to my legs?"

-The Supreme had intervened, so I do not know what was done. However, once we arrive at the cult, it will be released.

\textit{I had a feeling that my lower body was stiff, as if my pressure points were all clogged up. Seems like that son of a bitch pulled some shit.}

\textit{Motherfucker, I won't forget this.}

"Can't you just release it now? I promise I won't run away. It's just cramping way too much."

-The Supreme has already left. After all, he is one who particularly dislikes stifling circumstances.

Qing's eyes sparkled.

\textit{What did you just say? The fucker is gone?}

\textit{Master also has a deep knowledge of herbal medicine, so maybe I can just run and think about what to do afterwards.}

-Please do not harbor any vain hopes. There are two Transcendent Realm Masters here. And isn't your leg also in discomfort?

\textit{Damn it, just as I was getting all excited. It's fucking over.}

Qing pouted her lips.

\textit{Why the fuck are there so many Transcendents? Do they have nothing better to do other than kidnap just one little Peak Realm?}

-If you truly have nothing to do, why not learn a martial art?

"Martial art? What kind of martial art?"

-A Divine Art that the Orthodox Faction calls Demonic Arts.

\textit{First, they kidnap me. Now, they're yapping about Demonic Arts? The fuck is wrong with them?}

Qing was incredulous and retorted.

"Are you telling me to learn Demonic Arts?"

Qing had already mastered one of the eleven most heinous Demonic Arts Under Heaven, becoming a White Hand Witch who had grasped White Hand Demonic Arts.

-You shall learn it sooner or later anyway.

"Me? Why?"

-I shall be honest with you. We need to find at least one weakness in you. After all, is that not the only way we can let you go with peace of mind once everything is over?

"So you're saying if need be, you're going to spread rumors that I've learned Demonic Arts?"

-Still, learning it now would be better than being directly taught by the Supreme, wouldn't it?

It was a choice between just learning it or getting beaten into learning it.

\textit{Mmm. Well, then there's no real reason why I have to learn it painfully, right?}

Qing was quickly convinced.

After all, she had already mastered one, so what difference would another make?

Hadn't she also learned what to do when forced to learn Demonic Arts?

First, she would deny she learned it, and if that didn't work, she could just use her Master's name.

Since her Master had allowed it, what did it matter whether she learned one or two Demonic Arts?

\textit{I mean, what else can I do? They tryna threaten me into learning Demonic Arts at sword point, aren't they?}

\textit{Come to think of it, Master had also said that the more Lifesaving Absolute Moves, the better.}

\textit{I guess it's just like adding another secret weapon to my arsenal.}

Qing made a swift decision.

"Alright, I'll learn it. Whatever."

It was a rather refreshing response. So much so that it seemed nonchalant.

-...Are you being sincere?

It was enough to make those outside question her sincerity.

"I'm going to learn it anyway, right? Why bother hesitating? I might as well do something to pass the time."

-Very well. I will recite the Sutra to you now. \textit{Dark Sun Earthly Day and Night, Heaven Earth Great Reversity Black Slaying Death...}

The Sutra flowed from beyond the wall.

It was a transliteration of the most primitive and inconvenient characters, be it past or future.

Originally, ideograms were nothing more than messy scribbles used by primitive people before the birth of Christ.

Using ideograms was evidence of being not quite human. Basically, they were underdeveloped, a creature more like a primate that belonged in a spectrum between monkeys and true humans.

For that reason, Qing listened casually and let it pass through one ear. There was no need to pay much attention to it.

After all, once she heard it, the Martial Arts Window would register it automatically.

-\textit{...Sawoojiya}. Have you heard it all?

"What, that's it?"

-I shall recite it again for you. \textit{Dark Sun.}

Qing cut him off with a loud shout.

"Hey! Are you playing with me right now?"

The Martial Arts Window remained silent.

Qing could register a martial art in the Martial Arts Window just by touching its Secret Manual.

It was a kind of waiting state separate from actually infusing Practice Points to learn it.

However, there was a condition.

The Secret Manual had to be in a perfect and complete condition.

\textit{This fucker promised to teach me Demonic Arts. But what's this? He's trying to scam me, huh?}

-What is the matt-

"If you're going to recite it, why don't you recite it properly? You dare to play around with martial arts? Are martial arts a joke to you? Haiyaaaaa sheeesh, after all that talk about honesty, in reality you're just a fucking scammer, huh?"

Upon saying this, there was silence from the outside.

After a while, the voice returned.

-Bullshit. How fucking ridiculous.

Qing doubted her hearing.

What did you just say?

That puny little fucker dares?

Just because he isn't right before me?

-...I misspoke. Please do not misunderstand. It seems there was a mistake. I might have memorized something wrong, so I shall check again.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The owner of the most malignant Demonic Arts, Essence Absorption Demonic Arts, was called the Killer Among Killers.

The identity was a Demonic Human who was jointly subdued by the Orthodox, Unorthodox, and Demonic Factions.

Even if it wasn't that specific art, just mastering one of the Ten Great Demonic Arts usually came with a title.

However, a title was a relative thing, so what one side and their enemy called it differed.

To the enemy, she could be called the White Hand Witch; to her allies, the White Hand Divine Maiden.

Or perhaps the White Hand Demonic Queen.

Those who mastered Demonic Arts typically belonged to the Unorthodox Faction or the Demonic Path, so they took pride in a title that included 'Demonic'.

Only the Orthodox Faction frothed in rage at the thought of the Ten Great Demonic Arts Under Heaven.

Meanwhile, disciples of the Unorthodox and Demonic Path felt a bit envious, and rather admired and sought to obtain them.

Black Slaying Demonic Warlord, too, was a title that indicated the owner of such Demonic Arts.

Black Slaying Demonic Palm!

If hit properly, it wouldn't end with mere bruises but necrosis and decay of flesh.

The unique characteristic of a Black Slaying Demonic Human was quite literally their black hands.

After all, they were imbued with the power to rot living flesh.

Gaotang Shuang \footnote{高堂霜 Godang Sang}, the Black Slaying Demonic Warlord, paused as he tore apart dry meat with his black hands.

It was a little-known fact that the Black Slaying Demonic Warlord's given name was monosyllabic, thus ‘Sang'.

After all, Gaotang was a rare family name in China.

"She realized it was wrong just by hearing the Sutra?"

"Yes, Demonic Warlord."

"The Pavilion Leader is jesting with me, it seems? Is that kid some kind of Heavenly Miraculous Talent? How could she know it's wrong just by hearing the verses?"

Gaotang Shuang's tone was blunt.

Zhi Shengzhu responded carefully.

"There is a possibility that may be the case. She is a woman who has already reached the Late Stage Peak Realm, has she not?"

That was generally how Qing was viewed in Jianghu.

In fact, people had been so hoodwinked by her so-called ‘talent' that she could be called the Greatest Scammer Under Heaven. Who else could possibly reach her heights, after all?

"So, you suggest passing on the complete Sutra?"

Gaotang Shuang let his discomfort show.

Even if it was the Supreme's command, giving the incompletely twisted Sutra was already a radical break from the traditional conventions of Wulin.

But now, they even wanted him to pass on the complete verses?

"Why not think of this in a different lens? Once she obtains a Black Hand, she will not be able to return to the Orthodox Faction anyway."

That was precisely why they had chosen the Black Slaying Demonic Palm.

Appearance alone was enough evidence to prove someone as a Demonic Human.

‘Look at her hands. They're weird, aren't they?'

‘What the… She's a Demonic Human, isn't she? Then let's kill her.'

…was along the lines of what people would say.

"So, are you suggesting we take her as a disciple?"

"Ho-. What are your thoughts on such a proposal?"

Zhi Shengzhu managed to recover from his slip of the tongue.

Fortunately, the answer came off in a somewhat cutesy manner.

\textit{How fucking ridiculous. A Demonic Human? Taking on a disciple? What a joke.}

In the Divine Cult, a disciple was merely another term for a servant or an attendant.

They were expendable, a possession that was removed immediately if perceived as a threat.

Why? Because otherwise, a disciple might overthrow the teacher and take their place.

This was the law of the strong. And only the strong could survive.

It was a stern rule of the Divine Cult.

That was why Gaotang Shuang was so reluctant.

What if, after passing on his Demonic Arts to this Heavenly Miraculous Talent, she absorbed it all and threatened his position as a Demonic Warlord?

"Hmm. I shall think about it."

"Yes. However, I must dare to request a significant decision for the sake of the Divine Cult's greater cause."

That old fogey is being so tiresome.

Zhi Shengzhu thought as such.

How dare he act like he's something when he has no choice but to follow the Supreme's commands anyway?

In the Divine Cult, the Supreme's word was absolute.

The Supreme's martial status was in the Late Stage Unrestrained Realm.

But in reality, he had transcended that long ago.

After all, he had attained complete Divine Arts and after becoming a Demonic Human, he sealed his own meridians to reach the Demonic Descent Realm.

Even now, he was in a state where he could ascend to the Profound Realm and even beyond at a moment's notice.

The words he spoke to Qing were not mere bluster.

However, Zhi Shengzhu couldn't just tell Gaotang Shuang, ‘The Supreme commanded it,' and use that as a threat.

After all, that would utterly impair his honor and pride, thus making him lose face.

The only things more precious than face to a martial artist was life and their martial arts.

Thus, Zhi Shengzhu had no choice but to feign ignorance and plead earnestly to create some sort of justification.