\chapter{Who Would Threaten With A Sword… (7)}

Qing thought to herself.

\textit{I don't need to be cautious anymore! Who gives a fuck what others think?}

\textit{After all, I'm an important person!}

The Heavenly Demon Divine Cult underestimated Qing's ability to read the room a bit too much.

There was definitely a matter concerning the Fushen-di that needed handling.

Due to the lock/ unlock function, quite a miraculous feature considering the ever so primitive Zhongyuan, there was no one who could replace Qing.

\textit{Basically, there's no other choice besides me being the one to blow it.}

\textit{What if I say I don't want to?}

\textit{Then, well, fuck it. Let them wait for a few decades.}

So, Qing decided to blatantly fuck with everything they did.

\textit{It's fine as long as they don't say shit about how I only need my mouth and arms, like how that bastard, the Alleged Supreme or whatever, did.}

\textit{What did you say? Since my hands and mouth are the only parts of me that are necessary, it doesn't matter if I don't have eyes or legs?}

\textit{Then, I might as well throw a fit and act like I'd rather die.}

Moreover, her rehabilitation was progressing smoothly.

Judging from their reactions, it seemed she was doing so well that they might even give her a round of applause just from the mere act of walking.

As such, it was time to bide her time and wait for the right moment.

That was Qing's plan.

It wasn't just out of boredom that Qing smashed the head of a villain.

It was to probe gently, seeing what would happen and whether it was okay or not.

It was quite a big decision on her part.

After all, what if something went wrong and they tortured her?

Honestly, Qing was ready to wail, tears and snot streaming, as she obediently played 108 songs on the flute in a row.

\textit{But, what's this? There's no reaction, huh?}

So, she came to a conclusion.

\textit{Seems like they're more desperate than I thought, huh.}

\textit{Then, I need to fuck with them even more.}

Of course, it was also fun.

The Black Slaying Demonic Palm was a Palm Technique, just like the Buddha's Palm, but there were also differences.

It was a martial art that focused more on a type of palm strike called a Long Hit.

If asked about the pros, it would be the excellent feel in her hands when using it.

The sensation of shattering skulls!

The downside, though, was that the black hands were kind of gross.

It was way too black.

Not just some shade of brown or gray, but a color infinitely close to 100\% black.

Qing looked at her hands, now covered up to the back of the hand in black skin.

"Hoooo…"

As Qing exhaled, the blackness smoothly retreated into her skin.

A feature of the White Hand Demonic Arts was the Sword and Dao Invulnerability below the elbows.

The clean skin and the long slender hands were just side effects of this process.

And when using the Black Slaying Demonic Palm, she had to break through the almighty arm of Sword and Dao Invulnerability, the White Hand state, and gather Evil Qi in order to produce the Black Palm.

It was much harder than expected.

It was because the White Hand Demonic Arts had already settled in the proper direction of her Pressure Points.

To use the Black Slaying Demonic Palm, she had to twist these Acupoints.

A delicate task that required twisting the pure True Qi into Evil Qi, to boot!

Qing was hiding the fact that she could change the color of her hands as if waving a light stick from the Demonic Cult bastards.

After all, they thought that was the reason why she didn't run away.

For some reason. her mind was filled with only nasty, mean thoughts.

Either it was a feature of the Heavenly Slaughtering Star, or Qing was just that kind of person from the very beginning..

Anyway, by maintaining the Black Slaying Demonic Palm with desperate focus, she inadvertently increased her attainments in the martial art.

That was why Qing's Black Slaying Demonic Palm was growing rapidly.

At any rate, time passed swiftly.

\textit{Seems like about two months passed, right?}

\textit{I'm bored!}

During that time, she killed quite a few assassins.

As such, no one approached Qing.

Actually, those in the Covert Operations Division of the Divine Cult's Outer Hall were mentally elite, gathered only from the loyalists of the Divine Cult.

After all, living in the peaceful Zhongyuan but continuing to serve the Divine Cult was not possible with any ordinary mental fortitude.

These assassins, armed with endless hatred for Zhongyuan, mainly gathered intelligence and, as side jobs, engaged in human trafficking, robbery, and murder to provide significant funds to the Divine Cult.

Thus, they were too valuable to be killed off by Qing's misbehavior.

That was why they imposed a no-approach rule.

Zhi Shengzhu, that kiddo, also started to avoid Qing.

\textit{I was at least able to go about my day before by making fun of that little punk.}

\textit{It's slowly getting boring, though. I should just kill him.}

\textit{Tsk, tsk. Can't believe that little kid has already accumulated that much Evil Karma. What was he even thinking? He should pay for what he did.}

Right when Qing made up her mind…

The door of the carriage opened in quite a rude and abrupt manner.

Underneath the leather, there was an old man so skinny he looked like a skeleton, looking down at Qing with displeasure.

"Ah. Is it mealtime?"

Qing obediently extended her arm.

The old man grumbled and picked up Qing.

"You ill-mannered little brat. It is like the duties and morals that should be fixed in this world have been reversed. Has the world turned upside down? Even Yama would be startled at this sight. So much so that he would send you on a tour of hell."

"I know, right? Who told you to make my legs disabled?"

Qing was receiving care from the old man.

Yes, you heard that right. She was not giving care.

She was receiving it.

That was why he said it felt like the world had turned upside down.

This skinny old man was a Great Demonic Adept named Cui Liweng \footnote{崔李蓊. Choi Leeong (최리옹) in the original text}, known as the Purple Lightning Demonic Warlord or something.

Despite seeming like he could be knocked over with the slightest touch, he was a Master in the Late Stage Unrestrained Realm.

And he had an amount of Evil Karma that was fitting of him being called a Great Demonic Adept.

As Masters who were returning to the Divine Cult joined Qing's convoy procession, now there were four in the Transcendent Realm and one in the Unrestrained Realm.

As for the Peak Realm Masters? Their numbers were overflowing.

And that was just the number of Masters outside the cult.

Qing had underestimated the group known as the Heavenly Demon Divine Cult.

The Heavenly Demon Divine Cult, aiming to conquer Zhongyuan, was not all bark and no bite.

To be honest, her legs had fully recovered the day before yesterday.

However, the level at which she feigned illness had already reached the heavens.

Right as she thought it was the prime time to escape, Masters started teeming around, making her incapable of doing anything besides observing cautiously.

\textit{But by the way, to think that his name is Liweng.}

\textit{I keep thinking this, but… Isn't it kinda cool?}

"It is a relief that a peerless murderer like you is at least crippled in the legs. The Supreme indeed showed great foresight."

"What? You should think that I'm misbehaving because my legs hurt, you know? If they were fine, I wouldn't have lost my temper."

"Such a foul-mouthed, rude bitch. How completely rotten. If it wasn't for the Fushen-di, I would have fried you in shitwater long ago."

"Oho. Grandpa, watch your mouth, will you? I'm going to eat soon, you know? How can you say something so disgusting? There's mudwater and there's oil as an alternative. Why go as far as to resort to shitwater?"

Cui Liweng glared at Qing with a hollow look.

"Oho. Bad Grandpa. Don't open your eyes like that. I might get fond of you."

The glow in Cui Liweng's eyes grew even more sinister.

\textit{Damn, seems like at the Unrestrained Realm, even their eyes are no jokes.}

Even while feeling the pressure, Qing feigned indifference.

"…Looks like a bitch like you need to have all your flesh peeled off."

That was a threat to separate flesh from bone.

Slightly intimidated, Qing went out of her way to look around.

The open grassland was dotted with several large tents.

This was not Zhongyuan Qing knew anymore.

When entering one of the large tents, a lavishly set table and a cult-like gathering that swarmed with villains unfolded.

"Have you arrived, Elder Purple Lightning Demonic Warlord?"

The villains of the Divine Cult greeted Cui Liweng.

From what Qing observed, these evil people of the Divine Cult were actually more respectful than others.

She knew the reason for that.

She had seen a guy who made a fuss while drunk get his head smashed last time.

In this place, if you lacked manners, you would also lose your life.

"Elder, you should have just grabbed that crazy bitch by the hair and dragged her along, instead of treating her so preciously."

One of the Demonic Humans tried to suck up, before quickly shutting his mouth and lowering his eyes.

It was because of the purple lightning streaks emanating from Cui Liweng's entire body.

This was the Purple Lightning Qi unique to the Purple Lightning Demonic Arts.

Thanks to that, Qing got hit by a few streaks too.

Delivered to the table, Qing indulged in the only pleasure of her life—gourmet food.

As she greedily stuffed her cheeks, someone belatedly took a seat at the opposite side of the table.

"Uem, kidfwo."

With her cheeks bulged, Qing smiled welcomingly.

Usually, he would stealthily avoid her, but today, for some reason, he appeared right in front of her. Right on time. She had made up her mind to kill him, after all.

I'll hold back for now since there's a lot of Masters around, but just you wait and see.

Qing's smile was chilling.

Zhi Shengzhu started talking without even greeting her.

"Previously…"

"Woft?"

"You asked about the law of the strong."

Qing swallowed the food she had been chewing.

"What the… You've been thinking about that all this time?"

"I have pondered over it for a long time. However, no matter how I look at it, what the Young Lady did was merely an act of murder. It does not reflect the law of the strong."

"Really? Why? Because I'm not a disciple of the Divine Cult? Because it's okay for you but not for me?"

"That is not it. When the strong take the life of the weak, it must be a necessary act. At the very least, it should be a meaningful death that serves as nourishment for achieving a higher realm."

He must have thought very hard about it. However, unfortunately for him…

His opponent was once a production worker who proudly spoke the gospel of liberal arts.

A self-made giant who majored in humanities and secured a difficult position in production!

Hadn't she lived in a cruel society where humanities graduates barely eked out a living with continuous short-term contract jobs if they were not recipients of basic livelihood aid from the government?

What did this mean? It meant that the success Qing had achieved could be called, dare she say, mythical.

"You're saying it is a choice made by nature due to the law of the jungle? Natural selection? Like how a well-fed predator doesn't hunt? A natural cycle proven by the food chain? Is that what you're trying to say?"

"……!"

Zhi Shengzhu seemed to be struck by lightning.

"Well, whatever. If you say so. I guess that's how it is then."

Qing outright stopped paying any attention to him.

After all, there was no need to seriously respond to someone spouting dogshit.

It was a ridiculous thing to say in the first place.

How many predators hunt just out of boredom?

Look no further than the alleyways, where those furred cockroaches mistakenly called cats fucked around.

"By the way…"

Zhi Shengzhu continued to speak.

Right as Qing looked at him, wondering what dogshit he would spout next, she found Zhi Shengzhu expressionless yet… somehow smug.

\textit{The fuck? What's up with him?}

\textit{Is he thinking that he won just because I didn't talk back that much?}

\textit{No fucking shot he's thinking that, right?}

\textit{Then, I guess I have to show him the ultimate move in an argument. Picking at his words to make a personal attack.}

Qing readied this secret art, generally forbidden in a battle of words.

That's when it happened.

"About that hand."

"Huh?"

"Last time, it was definitely colored black up past the wrist, you see."

Qing was taken aback.

To be honest, maintaining the Black Slaying Demonic Palm was no ordinary task. And it only got more difficult the higher its realm was.

"I have been observing closely thus far. And from what I noticed, that blackness seems to fade significantly during meals, huh?"

It was unavoidable for someone to let their guard down while eating.

No, in the first place, is it wrong to want to eat comfortably?

Even dogs aren't bothered during mealtimes!

"Haha. Maybe there's something wrong with our little kiddo's eyes. Did you see incorrectly?"

"The Black Palm. You can hide it, can't you?"

Though it ended with a question mark, in reality, it was more of a statement made with conviction.

And there was no point in denying it; he wouldn't believe it anyway.

Qing sighed deeply.

\textit{Quick-witted kid. I should have gotten rid of him sooner.}

Even though she had decided to kill him, he was not a bastard she could just fuck up like she had been doing to the fodders.

This punk, despite appearances, was a high-ranking figure revered by even the prominent Masters here.

"Seems like I got caught, huh?"

The fault lay entirely in her own carelessness, yet she had the audacity to yap about how she was ‘caught'.

Qing's hand turned white again.

Clean and beautiful.

Once it transformed from its original black and unsightly appearance, it suddenly became an incredibly exquisite hand of a beauty.

As if expecting this, Zhi Shengzhu's usual lack of expression broke for the first time, the corners of his mouth lifting slightly.

And then, from across the table, the Black Slaying Demonic Warlord coughed in startlement, powerfully ejecting all the meat he had been chewing.
