\chapter{Who Would Threaten With A Sword… (1)}

Collect Yin Supplement Yang referred to the method of taking a woman's essence to stimulate Yang Qi, a technique practiced by men.

It was a cultivation technique from Daoism that promoted the joyful mutual growth of True Qi between men and women through the love of cloud and rain. A method commonly known as Dual Cultivation that benefited all.

However, it was revealed by the whims of some sick bastard's little… stick that the effect of increasing Inner Qi was hundreds of times better if only one side enjoyed it.

Thus, methods that harm the other party were considered evil, and those that were mutually enjoyable became a somewhat awkward and embarrassing knowledge for the sake of leading a happy household.

It didn't stop there. Jianghu was vast and people had various… tastes, of course.

Collect Yang Supplement Yang also existed. In fact, there were sects that actually specialized in this, but they were deemed public enemies of Wulin that were incomparably evil and disappeared.

In contrast, the Heavenly Flower Hall, famous for Collect Yin Supplement Yin, was classified as a sect of the Orthodox Faction and still operated normally, which showed that the people of the world had quite the double standard.

After all, even a collection of erotic paintings based on Heavenly Flower Hall was recognized as a legitimate subcategory of the pornography industry that existed in these ancient times.

And Collect Yang Supplement Yin also existed.

The most famous sect practicing it as its main method was the Bliss Palace.

Ever since the founder of the Bliss Palace, the Coital Witch Xian Youchun \footnote{先優春. Seon Wooseol(선우설) in the original text}, vowed to give men the happiest deaths, countless men have sucked their last breath under the crotches of Bliss Palace disciples.

As it was a method that harmed others for training, Bliss Palace was naturally designated an enemy of Wulin.

However, they escaped annihilation and fled far to the lands of Xinjiang, where they met the Demonic Cult, who happened to be raising the flag of invasion against Zhongyuan and fostering a spirit of revenge.

As such, joining the Demonic Cult was the natural course of action.

Currently, the leader of the Bliss Palace was known as the martial artist Xian Yue \footnote{咸月. Hamwol(함월) in the original text}, the Xi Shi Divine Maiden.

Xi Shi was known as the Most Beautiful Woman in History.

However, the title of Xi Shi Divine Maiden was rather a very good indication of Hamwol's thick skin rather than her beauty.

This was because she was the one to come up with the title of the Xi Shi Divine Maiden and even publicly called herself as such.

In response to that, the people of Zhongyuan resignedly went, ‘Haiyaa, whatever. If you say so, then it must be so. Fine, just be Xi Shi then,' and simply changed one little word in her title.

Xi Shi Retard Maiden, Xian Yue.

In the first place, she was a bitch who holed herself in the Demonic Cult, refusing to leave.

Some people even stated they would love to slice that shameless face just once, lamenting it as an eternal regret.

And in that regard, now was the opportunity to address such a grievance.

After all, the Xi Shi Retard Maiden Xian Yue had secretly infiltrated all the way up to Hubei Province.

"Hehe, to think I have to kidnap the disciple of the Godmother. This woman is not too keen on using such a nasty method against my lifelong rival."

The boy listening, the youngest Secret Pavilion Leader of the Demonic Cult, the Omniscient Iron-Mask Zhi Shengzhu \footnote{智勝主. Ji Seungju(지승주) in the original text}, thought with his characteristic expressionless face.

\textit{Fucking bullshit. What an absolute joke. A bitch who merely sucks out men's essence calling the Zenith Among Women her lifelong rival? When she is only at the Late Stage Transcendent Realm, even at her piss-old age?}

His true disdainful thoughts did not show on his face.

Zhi Shengzhu was famous for never having shown any expression throughout his fifteen years of life.

That was why he was called the Omniscient Iron-Mask.

An expressionless face as if wearing an iron mask.

And a mind that sat back and seemingly saw through everything.

Thus, combining the two, he was the Omniscient Iron-Mask Zhi Shengzhu.

"This must result in a success. The Supreme himself has descended, after all."

"The Supreme himself! Is it really true? Is the Supreme indeed here?"

Xian Yue's face became soaked in ecstasy.

"If this task succeeds, could this young girl receive the Supreme's grace? What do you think, Secret Pavilion Leader?"

Zhi Shengzhu replied.

"How fucking ridiculous. Young girl, my ass."

Of course.

Xian Yue's eyes narrowed.

"Secret Pavilion Leader. It seems that your inner thoughts and words spoken have switched again, yes? But… ‘How fucking ridiculous'? ‘My ass'? Could you possibly be saying that to this young girl?"

"I apologize. It happens sometimes. I tend not to talk much, so it has become a habit to mutter to myself."

Zhi Shengzhu apologized with his perpetual lack of expression.

This was not new for the Omniscient Iron-Mask.

That was why among the Demonic Cult, everyone knew Zhi Shengzhu's outward and inward natures were completely different.

Xian Yue seethed inside.

But another title for the Secret Pavilion Leader was the Demonic Brain.

It was the term used to refer to the personal strategist of the Supreme of the Demonic Cult.

Basically, this expressionless, cocky, twisted little kid was the right-hand man of the Supreme of the Demonic Cult.

Even though she seethed inside, Xian Yue couldn't do anything about it.

As Xian Yue simmered in rage, the little kid spoke again.

"A kidnapping can be performed without the Xi Shi Divine Maiden necessarily getting involved. But since it is that very Ximen Surin's disciple, taming her is a tall task. And one that is more crucial."

"Then, what if I accomplish that crucial tall task in addition to the kidnapping? Could I receive the Supreme's grace then?"

Lecherous anticipation flickered in Xian Yue's eyes.

Despite being called the Xi Shi Retard Maiden, her beauty could indeed shake the world.

Outwardly, she seemed like a sultry peerless beauty in her thirties.

Outwardly, that is.

\textit{What sin has the Supreme committed to have to deal with this sixty-three-year-old hag?}

Zhi Shengzhu hid his inner thoughts and replied.

"...If it truly comes to that, the Supreme might indeed take notice."

At the same time, he thought.

\textit{Ah. The position the Supreme holds is truly a pitiful one.}

Feeling pity for the Supreme, Zhi Shengzhu quickly changed the subject.

"So, you said there is a way to lure Ximen Qing far away?"

"Is there anyone as easy to handle as a brat who thinks she's a heroic expert of the Orthodox Faction? This young girl will personally step forward, so, Secret Pavilion Leader, just prepare to neatly tie up the bitch I lure out."

Zhi Shengzhu answered with his usual expressionless face.

"How fucking ridiculous. Young girl, my ass."

\textit{Of course.}

"Ah. My words came out switched again, my apologies."

\textit{Isn't this little fucker doing this on purpose?}

Veins popped on Xian Yue's forehead.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing, who used Qinggong, was incredibly fast.

But why was she moving at such speeds?

This was because, beyond those mountains, Sichuan awaited Qing.

And above all, numerous dishes laden with spicy Mala flavors were eagerly awaiting her arrival.

Ma and La!

It was a challenge of fiery hot flavors. Only the brave could dare to embark on such a trial.

And as a heroic expert of the Orthodox Faction, Qing was obligated to take on this challenge.

Right as her appetite was practically propelling her along the roads…

"Someone, please, help!"

It was a delicate voice that tugged at the heartstrings of men.

Although Qing was in a woman's body, her inner self was not.

Qing abruptly turned in the direction of the voice using the exquisite and miraculous Yue Maiden Footwork.

After pushing through the bushes, she found a half-naked woman exposed for all to see.

Her top was torn, nearly exposing all of her breasts, and her skirt was split up to her waist, revealing her underwear.

"H-Help, please help……."

"What is the proble- Mmmm."

Qing, not knowing where to look, gazed off into the distance.

Of course, her eyes couldn't help but wander around, sneaking in glances.

After all, overcoming instinct was not an easy task.

Then, the woman suddenly pounced on Qing.

The sweet scent of the woman's body overwhelmed Qing's senses, causing her mind to go blank.

"Uh. If you do this, it's a bit troubleso- You can't do th-"

"Heuk, heuuuuu."

The woman burst into tears in Qing's embrace.

Qing's hands flailed helplessly in the air before gently stroking the woman's back.

It was pure reassurance without any ulterior motive.

\textit{Ah. But by the way. She's hella soft.}

Qing had met and surveyed a wide range of city beauties while traveling with Peng Daesan.

Moreover, the beauty of the Divine Maiden Sect disciples who practiced Fairy Arts was extraordinary.

So she had actually just been wondering if her standards had become too high.

Yet even so, the beauty before her was incomparable!

But, what's this?

Suddenly, the woman urgently grabbed Qing's hand.

"Great Expert, please help! Bandits have entered my village and……"

It was a typical story.

Bandits had appeared in the village, killing all the men and raping the women.

Such incidents were not uncommon in Zhongyuan.

Qing slipped in an exclamation mid-story.

"My goodness, those sick bastards!"

"W-Will you h-help?"

"I'd like to cut them into little pieces and wipe them out right away. So, where are those bastards?"

"Ah! Thank you! Thank you. Truly……"

The woman clung to Qing and expressed her gratitude.

At the same time, Xian Yue thought to herself.

\textit{My oh my. How so very easy.}

\textit{Well, these so-called heroic experts of the Orthodox Faction are all the same.}

For women who had suffered, fellow female martial artists actually tended to be an even closer embodiment of righteousness and justice.

Those male fuckers merely claimed to be the Orthodox Faction. In reality, half of them would pounce with their 'sticks' if no one was around to see.

Of course, it was a technique Xian Yue used often herself, yelling 'Thank you for the meal!' and sucking them dry. But regardless, that didn't change how much of a disgrace it was.

There were many variations to this technique.

For some of the more righteous or prim men, acting like she was burning up from an aphrodisiac worked wonders.

They were fucking idiots.

The body would explode if the aphrodisiac wasn't relieved? Seriously?

If that worked, who in the world would ever use poison?

After all, with such a miracle drug, one just needed to feed them an aphrodisiac and watch idly by.

\textit{Now, if I lure this bitch deep into the hideout, I'm sure the martial artists of the Demonic Cult will handle the rest.}

"Then, this young girl will… guide you."

Xian Yue feigned pathetic helplessness and took the lead.

And right as she took one step forward…

Pwuuuk

"Euk."

Xian Yue shuddered.

Her eyes wobbled before slowly falling downwards.

The tip of a blade protruding between her breasts seemed to greet her with a smile.

As if saying, ‘Hello! Nice to meet you. I'm Blade Tip'.

Xian Yue was a martial artist of the Late Stage Transcendent Realm.

However, even the Transcendent Realm meant nothing in the face of a blade filled with Sword Qi stabbing her in the back when she was completely off-guard.

As she experienced her heart being torn apart, Xian Yue desperately asked.

"Why… How…….?"

"Mmm, because it's around four hundred points?"

"What… does that even……."

Xian Yue couldn't understand.

However, she felt wronged. Or rather, cheated.

\textit{I see, so you knew my face.}

\textit{Yes. Since you are the disciple of my rival, Ximen Surin, it's possible…….}

\textit{But how could a bitch of the so-called Orthodox Faction launch an ambush this naturally…….?}

\textit{She didn't have any change in her complexion, without even a sliver of killing intent…….}

That was as far as Xian Yue's consciousness went.

Thus marked the futile end of the vicious Great Demonic Adept who had sucked numerous men dry.

Qing pulled out the blade.

Ordinarily, martial artists would remove a blade in the opposite direction of insertion.

However, once the blade was inserted, Qing found that she preferred to remove it in a direction different from any of the sides it had entered.

Spurt!

The blade slid out from under Xian Yue's armpit.

Fresh blood gushed out profusely.

A fragrant aroma of blood that tickled the nose.

Qing took a deep breath, filling her entire lungs.

\textit{Huaaaaa, holy fuck! That's the shit!}

\textit{Right, this scent! I missed you so much……..}

Qing grinned sinisterly.

\textit{As expected! From the very moment I left, I did have a pretty good feeling about this journey.}

\textit{Can't believe some rando Demonic Adept exposed her back to me.}

Qing nodded to herself thoughtfully.

\textit{Is it my lucky day today? Yep, it must be, yep!}

\vfill
\begin{lstlisting}
	The chapter title reference to the Lost Ark meme. Essentially, an expensive in-game item is greatly nerfed, and people mocked those who are affected, saying nobody forced them to buy said item when its effect is still advantageous.
\end{lstlisting}