\chapter{Who Would Threaten With A Sword… (8)}

"No, how! How did you do it!?"

Black Slaying Demonic Warlord Gaotang Shuang shouted in surprise.

The Black Slaying Demonic Palm's Black Hand was a symbol of terror, as well as an indelible mark of a Demonic Human.

Wasn't that precisely why Gaotang Shuang wore gloves over his long sleeves?

It was a hand that he had considered beyond remedy, simply covering it up all this time.

But suddenly, the solution to such a problem appeared out of nowhere.

Gaotang Shuang cried out with deep yearning.

"How in the world!"

"It just did? When I did it, I guess? Why? You can't even do this? Ah. This is delicious. Grandpa, what is this?"

"Are you not even aware of what a dish is? Stupid brat. A dish is something you eat."

"Agh shit, what are you saying? I'm asking what's the name of the dish."

"Then you should have asked that. It seems you cannot even ask a question properly, you half-wit. That is Dymlyama."

Cui Liweng answered her.

But even though she got scolded, he actually seemed more like a grumpy, foul-mouthed granny.

In that sense, this grandpa, despite being a Great Demonic Adept, was oddly kind.

\textit{But why? It's not even like I did something that would make him like me.}

\textit{I just can't figure out what his intentions are.}

\textit{Well, I guess either way, there's no need to know about a Great Demonic Adept's circumstances.}

Qing gorged on Dymlyama.

It was a sweet dish made by roughly mixing vegetables and meat and boiling them until they turned soft.

There was no way it could taste bad.

After all this familiar taste… was braised ribs.

\textit{And with fried rice!}

\textit{I really like the local cuisine here.}

\textit{Though I'm not sure where exactly we are.}

Qing nodded her head vigorously.

Then she outright placed the entire dish in front of her.

Cui Liweng frowned.

"You seem almost desperate to display your uneducated nature. Even an animal would not exhibit your gluttony. You are truly a brat worse than even a bitch."

"Agh, shit. If you want to eat, just say you want to eat. Why all the rude yapping?"

Qing, using only her palm as a spoon, scooped up a large portion onto Cui Liweng's plate.

"Ha. Who said anything about wanting to eat?"

"You seem so old you can hardly chew, Gramps, so you might as well eat this since it's soft and doesn't need chewing."

"This bitch's muzzle is as filthy as a thoroughly rotten rag, it seems. Tsk tsk."

"So what? Did you help me clean it up or something? Nah, you didn't. So why do you care\~{}"

At the table next to her, Gaotang Shuang, who had become a dumbfounded onlooker, shouted angrily at Qing.

Surprisingly, the looks from those sharing the table, laden with fragments of meat in the dish, matched Gaotang Shuang's glare.

"Are you ignoring what this old man is saying!"

Qing picked at her ears as she replied.

"I'm talking with the elder here. Can't you see? Sigh. Know your place."

"What kind of conversation..., Senior. I apologize."

Just as Gaotang Shuang was about to object, he immediately bowed deeply upon seeing Cui Liweng.

To be more precise, it was because of the purple strands, Purple Lightning Qi, that faintly emanated from Cui Liweng's entire body.

Purple Lightning Demonic Arts handled True Qi that resembled lightning and were intrinsically biased towards Extreme Yang, as well as a Cultivation Technique dealing with Unorthodox Yang.

The world's hottest and most evil purple lightning.

The Purple Lightning Demonic Arts wielded True Qi similar to lightning.

As it was faithful in reproducing that destructive power, which normally could not be handled by humans, it was uncontrollable due to the inherently rebellious True Qi.

Thus, the owner of the Purple Lightning Demonic Arts would find Purple Lightning Qi spontaneously arising depending on their emotional state.

If in a bad mood, purple lightning would crackle and attack automatically, truly qualifying it as one of the Ten Great Demonic Arts Under Heaven.

Moreover, Cui Liweng was a Master of the Late Stage Unrestrained Realm.

If truly pissed, not just Purple Lightning Qi but Purple Lightning Force would leap across spaces.

The nature of lightning, after all, was to stretch a thousand miles in a flash.

And that was when Gaotang Shuang finally realized.

"How could a Female Expert from the Orthodox Faction be so unlearned and bark like a cur?"

"Agh, shit. I did learn well, you know? It's just that there's no one around worth showing courtesy to, so I don't use it."

"There is no one to show courtesy to? What is this old man, then? A scarecrow instead of a person?"

"Grandpa, you're not a person, though? You're a Demonic Adept."

"Hoho. You are a brat who will eventually end up burning alive because of the words you speak. When that happens, I shall joyfully throw a few logs in to help."

As Cui Liweng spoke, his Purple Lightning Qi was calm.

His harsh words did not reflect any real anger.

And the reason for that was soon understood.

The daughter of the Purple Lightning Demonic Warlord had died in his arms at about Qing's age.

'Ah, dotage strikes again!'

Since then, dotage had visited him occasionally.

Cui Liweng's daughter had been utterly rude.

And the Purple Lightning Demonic Warlord had treated his unruly daughter just like that.

So, when he saw any girl of a similar age with a missing sense of propriety, he viewed her as his own daughter.

Gaotang Shuang was dying to know how the Black Hand was removed but didn't want to agitate the senior, whose senility had been triggered.

He could always ask later.

Gaotang Shuang quietly sat back down at the table.

Meanwhile, Qing spoke without reservation.

"But rather than me, it looks like I'll be the one to conduct your funeral first, old man"

"Well, of course. A young brat should outlive an old man. From what I see, you shall soon set your own funeral date with that lack of propriety. But it is not just rudeness, is it? You ignorant girl, lacking manners."

"Agh, shit. Are you looking down on me? I've learned quite well, you know? Watch closely, Grandpa."

Qing displayed her dining etiquette refined under the pressure of nuclear bombardment.

With demure and elegant movements, she selectively nibbled only the meat from Cui Liweng's plate.

Thus, for a while, the Ximen Surin Trademarked Zhongyuan' Signature Beauty Table Manners was displayed.

A moment later.

In the end, Qing frowned.

"Haiya, shit. It doesn't even feel like I'm eating. When eating rice, I should still be able to chew it, after all. Anyway, you saw it, right? Wait, what the… What's the matter?"

Qing looked around, frowning.

The disciples of the Demonic Cult were staring blankly at her with a 'What did I just see?' expression.

Some were still rubbing their eyes, red from disbelief.

Even Zhi Shengzhu was gaping in astonishment.

To be honest, it was indeed a surprising scene.

Wasn't this the same girl who used to shatter skulls and lie down flat on their corpses?

Naturally, it was spine-chilling to see her suddenly acting like some celestial maiden.

Cui Liweng clicked his tongue in displeasure.

"A bitch who does not do something she can do is much worse than a cripple who is not able to. What are you showing off for, sitting there so proudly? Tsk."

Qing slammed her chopsticks down.

"Agh, shit. I can't eat because of all this noise."

And then, she quickly picked them up again and spoke.

"Ah. That doesn't mean I won't eat, though."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Gaotang Shuang was dying to know how the Black Hand was erased.

He was truly curious.

So, so curious!

But he never got a chance to ask.

Because after that meal, Cui Liweng began teaching Qing the Purple Lightning Demonic Arts.

After all, what was the reason Qing had learned the Black Slaying Demonic Palm?

It was so that its dark feature prevented her from returning to Zhongyuan, a ploy to keep her in the Divine Cult.

But now, they were aware that she could hide it.

As such, a different martial art was needed.

As it happened, Qing's personality was utterly fucked. It couldn't have been more shitty.

Moreover, the Purple Lightning Demonic Warlord was right beside her.

That's right!

The mood-dependent Purple Lightning Demonic Arts could replace the Black Slaying Demonic Palm.

After all, there was no way a Demonic Maiden throwing lightning bolts dozens of times a day could return to Zhongyuan.

Zhi Shengzhu thought so.

He couldn't be sure if attaching such volatile Purple Lightning Qi to her temper was the right thing for the world, though.

Opportunely, the senile Cui Liweng had started doting on her.

Zhi Shengzhu didn't need to persuade him all that much.

'Purple Lightning Demonic Warlord, perhaps you could teach your great art to Ximen Qi-'

'Understood.'

The agreement came before he even finished speaking.

Thus, by adding one plus one (plus another one that was a secret), Qing came to possess two (three) of the Ten Great Demonic Arts Under Heaven.

It was an unprecedented achievement in the history of Jianghu.

However, there was something even Zhi Shengzhu, with his brilliant mind, hadn't anticipated.

"It's one of the so-called Ten Great Demonic Arts, but it's Golden again?"

Qing was disappointed.

But still, she liked that it was an Inner Qi Cultivation Technique.

There could never be enough Inner Qi, after all.

Wasn't that Ximen Surin's teaching!

Qing reached One Star in the Purple Lightning Demonic Arts with Practice Points.

The violent Purple Lightning Qi settled into its new host's body.

The Purple Lightning Qi was the epitome of a completely fucked up and unruly lightning.

It was set to tear apart Qing's self-control and make her temperament even more volatile... but.

The already established two Divine Arts of Daoism were no ordinary art.

Zhu Xiang's Heart Cleanse Mirror, created by the Yan Emperor Shennong for his daughter, contained the Imagery of divine flames burning away evil.

Even among fires, there were hierarchies.

The Purple Lightning Qi, that was about to go wild, was harshly beaten and nearly extinguished by the fire.

At that moment, the temperate energy of the Yue Maiden Cultivation Technique, which had the power to embrace the Nine Worlds, stepped in.

It soothed and gently revived the Purple Lightning Qi.

Then, it set it in the most desolate, shabby, and dirty corner of the dantian, where drafts sneaked through due to how empty and trivial it was.

Jiutian Xuannü was tolerant of the Nine Worlds, thus embracing the, yet was strict in hierarchy.

Even worlds had their own order, after all. How dare a mere Demonic Art try to step out of its place?

As a result, the Purple Lightning Qi, without a chance to rage even once, was relegated to kneeling in a corner of Qing's dantian, facing the wall as if punished with a timeout.

If describing the clash of various energies inside the dantian in terms simple enough for a child to understand, that was how it roughly went.

This occurred while Qing was drooling, overwhelmed by the sensations that seemed to scoop and eat at her brain.

-How does it feel? Doesn't your body tingle? Hehe, just accept it. The Purple Lightning Qi often runs amok, after all. Though, you shall have to suffer a bit for a few days.

"Suffer? What suffering?"

-Isn't your body uncontrollably shaking and jumping? The explosive nature of the Purple Lightning Qi is supposed to make your body leap. As such, accept it as your fate and endure. It might be a severely painful fate, though.

That was what Cui Liweng said from outside the carriage.

Qing couldn't help but blink in confusion.

\textit{My body is shaking? Something is supposed to hurt? What?}

Qing drew out only the new violet True Qi, circulating it once through her meridians.

The energy, shy like a newlywed bride, timidly flowed through the meridians, completing a circuit back to the dantian.

\textit{For some reason, it kinda seems reluctant to stay in the meridians? Is that why it's returning to the dantian?}

"Uh. Is it normal to feel pain?"

-If the pain becomes unbearable, just tell me. I shall at least listen to your complaints. Hehe.

\textit{What pain?}

Qing was genuinely baffled.

But since the old man was expecting it, Qing decided to play along.

"Ah. It. Hurts. It. Hurts. So. Much."

-……?

"It. Hurts. Give. Me. Poppy. Me. Like. Now."