\chapter{Who Would Threaten With A Sword… (6)}

Zhi Shengzhu's shorter stature was a tightly hidden insecurity he held deep within.

Of course, sometimes his sentiments leaked out, so there were few within the Divine Cult who did not know about them.

However, no one dared to poke at the Supreme's right-hand man based on height.

But today, he had met his match.

"Alright. Then let's just say that our little kiddo has a long upper body."

"...If you have nothing else to say, then I shall take my leave."

"No! Stop! I have something to say, okay?!"

"What is it?"

Zhi Shengzhu's voice was brusque.

Qing asked with a faint laugh.

"About that saying. The Divine Cult follows the law of the strong, right? The strong are just, and those who survive are the strong?"

Upon seeing her black fingers, Qing immediately realized she had been fooled.

When she questioned if they had deceived her, they responded that with Qing's abilities and promising future, she could certainly enjoy power at the core of the Divine Cult.

And that was when the Divine Cult's law of the strong was explained to her.

It was a very fascinating concept to Qing.

The Heavenly Demon Divine Cult follows the law of the strong.

A group that worships strength.

The strong can have anything,

The weak have the right to prove themselves through challenges.

Perhaps, it was natural for Qing to be interested.

Because she was a Master.

Though now, well, how to put it… Her confidence was a bit shaken.

Anyway, it was precisely at this time that the question about the cult's commandments came up.

And being an executive of the Divine Cult, he couldn't omit explanations regarding its commandments.

"Yes. That is right."

"I've been thinking hard about it, you see. If that's the case, I haven't really done anything wrong to you all, have I? That Advance… Wave?"

"Do you mean the Advance Blue Brigade?"

"Yeah! Them. Sure, I annihilated them. And yes, I killed the Bliss Palace Leader. But that's just because I'm strong, right? According to your logic, since the strong me killed them, there's no problem, right?"

"That is correct."

"Oingggg? Really?"

Qing was about to follow up with a detailed description of the unsightly state of the Advance Blue Brigade and how they were dealt with.

After all, she had been thinking of provoking him further.

\textit{But what's this? There's no problem? Then…? Why?}

Suppressing her rising fury, Qing asked.

"So, there aren't any problems, yet you leave people in this state?"

"How shameless. You took the Supreme's property without permission. Moreover, you talked back to him. Rather, you should be grateful for the Supreme's mercy. After all, he spared your life."

"Ah. Is that what it was? Since I was weak yet dared to defy that Alleged Supreme?"

Qing grimaced.

That motherfucker.

"How dare you call him the Alleged Supreme. Such irreverence wil-"

Qing cut off Zhi Shengzhu's words.

"So, there aren't any regrets or dissatisfaction because I killed your people?"

"The commandments of the Cult follow the law of the strong. As such, there is no reason for regrets. It is just that Young Lady Ximen was stronger."

Qing smiled broadly.

For some reason, it was an unsettlingly ominous smile.

"Good to know. Anything more to say? Can I return to the carriage now?"

"There is nothing more. Please return."

"Ah. I'm all drained and tired from coming here. It would be nice if someone could support me."

Zhi Shengzhu, still expressionless yet somehow clearly showing annoyance, waved his hand as if shaking off water.

An assassin from the Covert Operations Division silently slid next to Qing.

Qing spread her arms as if asking to be held.

It was the moment the assassin bent his waist.

Crack!

Along with a spirited sound, the assassin's head burst open like a watermelon, scattering in all directions.

"Hoooooly. Wow. Black Slaying Demonic Palm, yeah? This feels quite nice, huh?"

Qing, covered in debris, laughed.

Then after groping the head a bit, she found the long, dangling optic nerve and squeezed it tightly.

Even Zhi Shengzhu, who had seen the Supreme's cruelty, felt chills run down his spine.

He tried to hide it under his usual expressionless facade.

However, his shout came out a beat too late due to how surprised he was.

"W-What is the meaning of this!?"

"Me? I'm strong and…"

Qing pointed to the headless corpse.

"That thing. Was weak. That's the law of the strong. Mhm. Yep, yep."

And then, she shamelessly nodded her head.

\textit{A Female Expert of the Orthodox Faction? This person?}

\textit{She's saying something a Demonic Human would say...!}

Zhi Shengzhu inadvertently got the answer right.

However, Zhi Shengzhu, unaware that he had guessed correctly, yelled out.

"That sort of action is not the law of the strong! The strong should not torment the weak without any reason!"

"Oing? Hehhh? Was that it? Kyaaa. Wow. Didn't know that."

"Is that not obvious? If your actions are the norm, no one in the world could possibly survive!"

"Okay, okay. I got it. Could you not get so heated? You should have just explained properly. I thought if someone was strong, they could do anything."

Zhi Shengzhu was at a loss for words.

\textit{You're saying this is my fault? Bullshit, what kind of bitch is this!}

"I'm tired after exerting myself. Help me move."

"How can you say that even after causing this atrocity?"

"Aghh. I told you, I didn't know, okay? You're being so petty. Fine then. I won't go either. Shengzhu can go live in the Divine Cult. Imma just stay here."

"Bullshit, what kind of bitch is this…"

"Ah, I dunno. I don't care either. I'm tired. Should I just sleep here?"

With that, Qing jumped off the chair.

Describing her action as ‘jumping off' was actually quite accurate as she couldn't steady her legs.

She then rolled on the blood-soaked floor and laid her head on the torso of a headless corpse.

"Wake me up when it's time to leave."

A crease formed between Zhi Shengzhu's eyebrows.

It was a huge incident. Any member of the cult witnessing this would be shocked speechless.

After all, the expression on the Secret Pavilion Leader's face had scrunched up!

"Damned bitch! Someone take this woman away!"

But the assassins from the Covert Operations Division just looked at each other, none daring to move.

It was understandable.

The colleague they had just been eating with was now rolling on the ground as a piece of meat.

"What are you idling for!"

"Right, right. Exactlyyyy. It was just one mistake, okay? It's because they didn't properly understand the law of the strong or whatever it was. So, don't be so scared. Okie?"

Qing added a taunt.

Zhi Shengzhu fumbled for the right words to say, before taking a deep breath in and out.

"Hooo. Escort the Young Lady. Hurry."

Anger tinged Zhi Shengzhu's voice.

In the end, the unfortunate youngest, unable to bear the imposing glares of his seniors, slowly crept closer with a reluctant expression.

The youngest assassin's hands trembled as he picked up Qing.

Then, a voice was heard.

"Ooooh. You score one hundred fifty points. Somewhat decent. However… Begone, head. Yap!"

It was the last sound the assassin heard in this world.

Because without a head, one no longer had the ability to hear.

Thwack!

Qing rolled on the floor.

It was because there was no one alive left to support her.

The headless youngest fell over her.

Qing, who was suddenly pinned down, let out a wheezy breath.

"W-What is...!"

Qing pushed the corpse away and responded.

"Hoit. Why? What?"

"What is this madness? You clear said it was a mista-"

"No, no. Hear me out. A man I've never seen before dared to touch my body. A woman's body. You feel me?"

Zhi Shengzhu was rendered speechless.

\textit{What in the world?}

"A weak bastard dared to mock the strong, so the strong killed him. That's the law of the strong, right? Do you acknowledge it? Yes, I acknowledge it. If so, you have been found not guilty. Bang bang bang."

Qing yapped nonchalantly and rolled again to lie down using the corpse as a pillow.

Her entire body was bloodied and bits of what used to be brains were scattered around her.

"That kind of thing is not the law of the strong! What kind of dogshit are you spouting to defile the commandments of the Divine Cult!"

Qing answered indifferently.

"Why? What about it? The Alleged Supreme was about to take one eye and two legs just because I talked back. So, are you telling me it's the law of the strong when he does it, but I'm tormenting the weak when I do it?"

"How dare you, to the Supreme…!"

Qing shook her head.

Blood spurted from the neck of the corpse in sync with her movements.

"See? It's fine if the Supreme does it and everyone else can't, right? You really need to explain it clearly from the start so I can understand. So, what's the standard? Starting from the Transcendent Realm and above, can you just kill anyone you want? Or is it starting from the Unrestrained Realm? What about the Profound Rea… Nevermind, that doesn't make sense."

"The Supreme is a being who shall resolve the enmity that the Divine Cult hol-."

"Agh shit. Fucking hell. Who asked about the Supreme? I'm asking what exactly is the law of the strong? You say it's the laws of the Divine Cult, but is it something only the Supreme doesn't have to follow? Is it something like that?"

"How many times do I have to tell you that the law of the strong is not-!"

Qing overpowered Zhi Shengzhu's yells with her own shout.

"SKREEEEEE!! Then what is it? Do you think being loud makes you right?"

"The law of the strong is, the law of the strong is…"

Zhi Shengzhu's words trailed off again.

It was the commandment of the Divine Cult that the strong survived.

The Divine Cult revered strength as justice and, as a result, gained the power to influence Wulin.

Its history of four invasions proved this.

The Heavenly Demon Divine Cult, as a single entity, waged war against the entire Wulin of Zhongyuan.

Despite being one against many and ultimately facing defeat, it left a mark in history four times.

The strong could dominate the weak.

They had complete control over life and death.

However, the weak also had the right to resist.

Thus, the weak who overcame the strong grew to become new rulers, more than entitled to their power.

\textit{So what about this woman?}

Following the Cult's commandment regarding the law of the strong…

Zhi Shengzhu's heart sank.

\textit{Was the Supreme's punishment too extreme?}

\textit{No. No one would say he had gone too far.}

Even if it was just one fighting unit, an entire brigade had been annihilated, Fushen-di had disappeared, thus causing a shift in the grand strategy, the Bliss Palace Leader had been killed, and the entire essence of a sect had burned and vanished.

Considering all that, one might say the Supreme had actually shown mercy.

But had all the actions the Supreme had taken been such a way?

What about the other Pavilion Leaders, the other Demonic Humans?

The now deceased Bliss Palace Leader had immediately assaulted any halfway decent-looking man she passed by, sucked up his lifeforce, and killed him.

The Demonic Doctor recently found amusement in creating zombies.

The Sura Demonic Sword was a madman who would not go to sleep unless he had slain a maiden each day.

Yet, no one criticized them.

After all, they were all the powerhouses of the Divine Cult and the vanguard in conquering Zhongyuan.

A force perfected under the law of the strong.

In the end, Zhi Shengzhu found himself unable to respond.

And Qing looked on at his dilemma, a sneer playing across her face.
