\chapter{Journey to Kaifeng (3)}

In truth, Qing didn't usually go around memorizing people's faces.

But it was just the beginning of spring, and the weather wasn't much different from winter.

There was a man with his upper body bare, striking a muscle-tensing pose and showing off his huge naked body to the outside.

Someone immediately came to Qing's mind, thinking 'Ah, that guy'.

"Excuse me, server. Is there perhaps a Zhuge…"

\textit{Ah. But what was his name again?}

\textit{I can only remember his surname Zhuge.}

"What was it, his title was something like Beast Man?"

At this, the server's eyes narrowed.

"Do you mean Great Expert Beastly Sage?"

"Ah! That's right. That's it. Beastly Sage! The body of a beast and the brain of a sage! Wow, I think I only heard it once, but I got it right. That's correct, right?"

"Well, I basically told you everything…"

The server looked at where Qing's eyes would be behind the face veil with an expression that seemed to ask where her conscience was.

"Then, could you go up and ask if he remembers this Sister who came, and if he does, if he could just save one seat? I'll pay for my own food."

"Well… He's an important person, how could I…"

The server looked troubled.

The most famous Wulin sect in Wuhan is undoubtedly the Wudang Sect.

Wuhan's pride, Wuhan's dignity, the leader of the Orthodox Faction and the Northern Dipper of Mount Tai (the position of Orthodox Faction leader usually changes depending on the locals), the Wudang Sect!

However, if you ask who rules Wuhan, everyone says it's the Zhuge Clan.

Because their territory overlapped with the Wudang Sect, they moved to a scenic spot next to Donghu Lake in front of Wuhan and established a new headquarters 800 years ago.

At that time, the government's orders were absolute, so they had no choice but to follow the Emperor's order saying, 'Since you two are stuck together, it's awkward to give land, one of you should yield a bit.'

So the Zhuge Clan stepped forward with a very bright, beaming expression, saying they would yield first.

In fact, even if they received the same amount of land, the area in front of Donghu Lake was such a good location.

Not only was it along the Yangtze River and by the lake, but the Huguang Plain around Wuhan was the most precious fertile land in Hubei.

The Wudang Sect couldn't abandon Mount Wudang no matter how much they coveted good land, so in the end, the Zhuge Clan swallowed up all the expensive urban and metropolitan land.

At that time, the level of martial arts wasn't high, and it was an era when the Greatest Master Under Heaven was only at the Transcendent Realm, so the influence of the Zhuge family members taking official positions and generously distributing benefits to their main family must have been significant.

"Ah. He really is someone I know."

Since the server had been consistently polite, Qing read his discomfort and couldn't force the issue.

After all, it was like calling over a new recruit who had just gotten their yellow tag and saying, 'I don't remember the name of your battalion commander, but anyway, tell him I'm here,' which was quite suspicious.

At that moment, Tang Lan-Ah stepped forward, using a villainess's specialty: pointing fingers.

"Hey, server. You're just a server, yet you're hesitating when our Qing'er is speaking? Go tell Little Brother Zhuge that the Speaking Poison Flower of the great Sichuan Tang Clan has dropped by."

"Ah. Yes, understood!"

The arrogant and high-handed tone, "Sichuan Tang Clan," and "Little Brother Zhuge."

This was the attitude that gave the server the trust that 'Ah, this young lady is certainly a high-ranking person'.

"What? You knew Zhuge?"

"Just by face. Maybe saw him twice? What about you?"

"I just saw him once too. He talked a lot, but he seemed nice."

"Is that so? He was quite friendly. Didn't act obnoxiously either."

He was certainly someone with an unusual personality, as there was no prior appointment and they weren't particularly close.

Yet as soon as the message was delivered, he came running down himself, which gave an idea of his character.

However, Qing can't help but think it might have been better if he had put on some upper clothing before coming.

"Oh, Sister Tang! What brings you to Wuhan! You must be on your way to the Wulin Conference! But how did you know I was here! Ah! Embarrassingly, you must have seen this little brother emitting his lofty spirit while looking out over the area! And the companion next to you also looks familiar. Ah! Sister, it's Sister, right? The one I met in Luoyang!"

He asked and answered his own questions, and even correctly guessed the identity of Qing, whose face was hidden.

This was the terrifying power of the brain possessed by the Zhuge family, the Miraculous Zhuge.

Of course, anyone with good observational skills could have quickly guessed from her tall stature and chest.

How many women in Zhongyuan would have both such rare height and rare chest size?

In fact, covering her face made her even easier to recognize.

"Oh, hey Zhugeie. You remembered?"

"How could I forget? Women skilled in debate are rare in this world. Come, let's not stand here, please come inside."

"Oh, is that okay? We're not pushing out other guests' reservations or anything, right?"

Qing said this as she entered the restaurant.

Zhuge Lixian laughed heartily.

"Sister, you are truly kind! But do not worry, the restaurant only goes up to the fifth floor. The sixth floor is used by our clan as a watchtower, which this little brother often uses for training. Of course, it's also a place to entertain precious guests. Like now."

"Oooh."

It turns out the Zhuge Clan had been continuously rebuilding the Yellow Crane Tower, which had burned down several times.

One might wonder why the building burns down periodically, but the Yellow Crane Tower was originally built as a watchtower for surveillance and is an important military facility.

Military facilities tend to burn down when the world is in turmoil, to the point where it was jokingly said that as soon as the Blood Cult or Demonic Cult showed up, the Yellow Crane Tower would be the first to burn, lighting the beacon fire.

Every time they rebuilt it, they increased the number of floors according to improved construction techniques, and incidentally opened a business as a leisure space.

Only the highest floor is used as a watchtower, as well as a clan rest area, as well as a banquet hall.

In modern terms, it would be like a penthouse.

"Ah, now you're Sister Ximen! To think you're studying under Godmother Ximen Surin! Oh, then Sister, aren't you at the level of a Sect Leader of the Nine Sects? This little brother should pay his respects with a grand bow!"

"Come on, no need to be so formal between us."

"Haha, then this little brother shall treat you with the protocol befitting a Sect Leader today! You originally enjoyed fine cuisine, didn't you? When it comes to Hubei, it's all about rivers and lakes, and Wuhan is at the center of it all, so today we shall dry up the fish population!"

"Our Zhugeie always knows just what to say."

At this, Tang Lan-Ah linked arms with Qing and spoke.

"I, I can buy lots of dishes too, you know? I'll even call the Greatest Chef Under Heaven and just…"

"Why would you bother someone who's doing business properly?"

"Sworn Sister, I, I'll work hard to earn money."

Jian Buxi clung to the other side as she spoke.

"Your friendship is truly deep! Now, this is the top of the Yellow Crane Tower, Piercing the Sky and Reaching the Clouds. This name comes from the sky of Chu that Sun Zhongmou yearned for in his heart. When hearing the word Chu, there are several it could be referencing, however, considering the historical context and the characteristics of the person, the academic consensus is that it refers to Xiang Yu's State of Chu…"

"Ooh. How amazing."

In Qing's memory, she roughly remembered him as a huge muscle man who talked a lot, and she was absolutely correct.

Qing let the words she couldn't understand anyway and wasn't interested in go in one ear and out the other, enjoying the view from the high place.

Although they had stopped at famous places wherever they went, there hadn't been a place this open and refreshing among them.

It was a skyscraper built high on top of an almost uniquely protruding mountain amidst the flat plains surrounding the naturally low-lying area of rivers and lakes.

The view from its peak was bound to be special.

"Ugh, this is in the way."

Qing casually took off her face veil and naturally handed it to Jian Buxi as if it were obvious.

Jian Buxi very naturally took care of the face veil.

At this, Zhuge Lixian made a fuss.

"Ah, Sister! My goodness, the Five Flowers of Wulin should become the Six Flowers of Wulin! However, as you know, while five is a perfect and auspicious number, six is an inauspicious number, so hmm, interesting. Perhaps one of the existing Five Great Beauties might have to unfortunately relinquish their title."

It was a remarkably plain attitude for making such a fuss.

Tang Lan-Ah immediately growled like a Chihuahua.

"What? You. Are you hitting on our Qing'er right now?"

"How could this little brother do such a thing? Doesn't Sister Tang know?"

"Know what?"

"Oh my. Haven't you heard? How this little brother is famous for valuing a person's inner beauty more than their outer appearance?"

"Hmph. All men say things like that. That a good heart is more important than a pretty face and whatnot."

"Hmm? You speak of a good heart? When it's already difficult for people to accurately know their own hearts, how could one measure and judge another's heart as good or bad? And since people's hearts naturally become generous to those they know, wouldn't the heart shown to the most beloved and mutually adoring person be considered beautiful for any couple under heaven?"

Tang Lan-Ah made a slightly disgusted expression.

It was clear she was thinking, 'Why does he talk so much?'

"Th-Then what, you said inner beauty?"

"That's right! A person's inner beauty! A person's beauty undoubtedly comes from their inner self! Isn't it from their bones and muscles? A strong physique is truly beautiful!"

Simultaneously, Zhuge Lixian bent his arms like sickles, raised both elbows horizontally, and twisted his waist to show off his bulging back muscles.

Qing thought as she looked at this sight.

\textit{Honestly, it's cool.}

\textit{I don't think even that actor-turned-governor\footnote{A certain Mr. Terminator} back home in his prime could be quite like this.}

Then suddenly, a thought occurred to her.

"Does Zhugeie prefer women like Young Lady Peng?"

"Ah! Embarrassingly, this little brother once ardently admired her. However, besides the age difference, Sister Peng said she had already married the Dao and had no space in her heart for men, so it's just a beautiful memory from my immature days."

Zhuge Lixian calmly reminisced about his past love.

\textit{This kid definitely has that aura. He's locked the fuck in.}

Qing nodded.

In fact, this love for physique in the Zhuge family is famous.

The hidden title of Hwangbo, the third family matriarch and Zhuge Ihyeon's mother, was 'Great Bear, Great Woman', like a big bear woman, so you can imagine how it was.

There was even a joke that if a girl had a large build, she should first learn External Arts and then loiter in front of the Zhuge Clan's main gate.

However, whether it was a curse of the bloodline or something else, none of the direct male descendants of the Zhuge family were born with both an outstanding physique and outstanding intellect.

In over a thousand years of family history, Zhuge Lixian \footnote{諸葛李賢. Jaegal Ihyeon (제갈이현) in the original text} was the only one.

He surpassed all his impressive older brothers, to the point where even those brothers willingly gave up the position of Young Clan Lord, saying the future of the clan rested on him.

Of course, Qing didn't know this, and neither did Tang Lan-Ah, who had never left Chengdu in her life.

"Ah, right. What about that tiny person?"

"Do you mean Elder Brother Uncheok? Of course, he's at the main family in Jinan. Ah, haven't you heard the news? They've set an auspicious date for the wedding this autumn. He'll be attending the Wulin Conference with his fiancée."

"Ooooh. Will they be throwing candy?"

"Haha, since you're a great elder of Daoism, Sister, if you attend and grace the occasion with your presence, my brother would be overjoyed."

"That works out well."

\textit{I can take Changming along after the Wulin Conference is over.}

But where's the wedding venue? It shouldn't be too far, right?

For reference, Qing doesn't know this (she really doesn't know anything, to be fair), but the location of the Hwangbo Clan is Jinan, the capital of Shandong Province.

It was close on the way there along the Yangtze River, but far on the way back, so the probability of Sect Leader Wang Zhuxi of the Divine Maiden Sect allowing Chen Changming to go out was exactly fifty-fifty.