\chapter{Journey to Kaifeng (5)}

\textit{Look at this little brat being so cheeky.}

But as they say, age is power, and the coquettishness of a seven-year-old girl was just adorable.

In fact, it's human nature that if it's not your own child, it's enough if they're cute and pretty right now.

That's why other people's dogs and cats are cute.

Or it's like how grandparents unconditionally dote on their grandchildren.

The scolding, education, and behavior correction that might be disliked are the parents' job; they just need to adore them.

Zhuge Xiang grabbed Qing's fingers and pulled.

Her tiny fist could barely hold two fingers and was full.

The child's unique warm body temperature was transmitted to Qing, whose hands were cold due to the side effects of Demonic Arts.

Qing pretended to be dragged along and spoke.

"Hey. But what if it's not a lie? I may not look it, but I'm a great elder at the level of a Sect Leader of the Nine Sects, you know? The crime of daring to deceive an adult is very serious."

"Ah. Really?"

"Really."

"Th-Then if Sister is right, you can specially marry our Gege…"

"Huh? Are Wulin practitioners supposed to bet on other people's positions? Your Gege should find his own marriage partner."

"Oh. Then what?"

Qing smiled wickedly.

"Xiang, was it? If I'm right, then Xiang will marry me, okay? How about as my second concubine?"

It was a mischievous joke that only an uncle would make.

Gulp. The child swallowed hard.

"But between women…"

"What, you can't do it? Then I should go back."

"Eek, you're just bluffing to make me give up now, right? The 36th stratagem, retreat to advance! Hmph, do you think I'm a little kid who doesn't know military tactics?" 𝖗

Zhuge Xiang puffed and led Qing.

Somehow, despite the winding and similar-looking scenery, she managed not to get lost and led the way skillfully, finally reaching a wide garden with a well-decorated lake.

And on one side, iron balls piled up by type caught the eye.

They were iron balls with handles for easy lifting.

"Here. This is a 100-catty iron ball. Now, let's see if you can lift it with one hand as you said… Oh, you're lifting it…"

"Ah. So this is 100 catty? It's quite heavy, huh?"

100 catty was already more than double the official world record (53kg) by Qing's hometown standards.

"But is this based on fruit or meat?"

In Qing's hometown, they still used a primitive and stupid unit system where the catty weight varied by item.

The Chinese people of the same era adjusted the catty weight to match the times (600⇒500, unified for all items), so this was one aspect where the Korean people should emulate their proactive and progressive future-oriented attitude.

Of course, this is the primitive ancient uncivilized Zhongyuan, so it's before the adjustment of catty weights.

"…?"

"At this rate, I could probably lift 200 catty too. Which one is the 200-catty one?"

Zhuge Xiang looked around and said,

"Th-There's no 200-catty one. Only 250 catty…"

It was clearly a lying face to anyone who saw it.

Qing chuckled and said.

After lifting 100 catty, she felt like she could lift 250 too.

"Which one is the 250-catty one?"

"Th-That one…"

Qing grasped the 250-catty iron ball with one hand.

It was manageable just to hold and stand, but when she tried to lift it above her head, her hand trembled and it wasn't easy at all.

Even for a body that had transcended human limits, it was creaking and straining.

Still, somehow she managed to fully bend her elbow and push with her shoulder strength to lift it high into the sky.

It was a miracle performed without even using momentum.

It was truly a heroic posture that would dominate an era!

At this, Zhuge Xiang's mouth opened stupidly, and conversely, her eyes sparkled brightly.

At that moment, Qing felt a sound resonating from inside her body, going 'tok tok'.

Startled, Qing immediately dropped the iron ball behind her, on the opposite side of Zhuge Xiang.

THUD!

When the 250-catty iron ball hit the ground, not only was the sound loud, but the vibration of the ground caused large waves in the pond.

"Wow, I can't lift it twice. That was too much."

Having directly felt the sound of muscle and tendon rupture, it seemed she wouldn't be able to use her right arm properly for a while.

She deeply regretted showing off unnecessarily and only hurting herself, wondering what on earth this was all about.

"How about that, kiddo? If it's 250 catty in one hand, that counts as 500 catty with both hands, right?"

Suddenly realizing her situation, Zhuge Xiang answered with a pale face and a whimper,

"Uuu, th-this concubine greets my lord, sniff…"

"Hey, what's this? If you cry, what does that make me? And am I that unlikable?"

"But, I'm a concubine, sob, and the second one at that."

"Speak properly, will you? Is it that you don't like being a concubine, or that you don't like marrying me?"

"B-Both are bad…"

"You dislike me that much? I'm hurt. Xiang is about to be neglected as soon as she becomes a concubine."

"Then at least make me the principal wife… sniff."

A tear, finally formed in the child's characteristically large eyes, dropped.

Qing tried to scratch the back of her head, but with a short "Ack!" she immediately used her left hand instead.

It seemed her right arm was more injured than she thought.

"Well, the night wind is cold. Let's go back, kiddo. We need to consummate the marriage."

Qing lifted Zhuge Xiang with her uninjured left hand and held her in her arms.

The little one clung to Qing's neck and started wailing loudly.

Qing had quite a mischievous side to make the child cry like this, but in fact, looking at her actions, she was overtly a bad person.

However, although this little Zhuge Xiang was knowledgeable and could recite even unfamiliar characters fluently, the fact that she readily believed such an absurd joke and burst into tears was truly befitting of a seven-year-old child.

"Hmm? But I don't know the way? We might get lost and become missing children who die if we're not careful. Won't someone guide us?"

At this, Zhuge Xiang's ears perked up.

"Ah. This is troublesome, very troublesome. If someone could show us the way, I might be able to grant one wish."

Zhuge Xiang immediately took the bait.

"Oh, then, sniff, I'll show you the way, so please forget everything… sniff."

"Haah. I guess it can't be helped. I thought I was going to live happily ever after with a pretty new concubine. Now I see this tiny strategist girl led me to an unknown place knowing this would happen. As expected of a Zhuge family strategy. I've been had."

"H-Hmph. You've only just realized… sniff."

Zhuge Xiang said with a bright red face.

"Aww, you're so cute. Ack."

Qing tried to pinch the chubby cheek characteristic of children but only let out a short scream due to the alarming pain in her right arm and gave up, walking forward.

\textit{But, my right arm isn't moving?}

\textit{Is this really okay?}

\textit{Isn't there some Hidden Dragon Tournament or something to attend?}

Somehow, the pain that kept coming as time passed was no ordinary thing.

Qing tried hard to ignore the chilling sensation running down her spine.

\textit{Right, there's a physician, so what's the problem.}

\textit{And well, one left hand should be enough.}

As such, here they were, a clumsy adult who properly ruined one arm just because they wanted to tease a little child.

"Alright. Let's go. Which way?"

"That way."

Meanwhile, Zhuge Xiang, whose tears had subsided, finally started to subtly inquire about Qing's background.

"Sister, how old are you?"

"Me? Twenty. I decided to be twenty."

It was an unreasonable number brought about by Ximen Surin's greed.

How cool would it be if a disciple of just twenty years, in her prime, easily swept away the formidable Hidden Dragons and won? It would also be a giant step for female martial artists.

It was part of Ximen Surin's women's rights advancement plan, thinking that if the world knew the Greatest Talent of All Time was a woman, all martial artists would no longer be able to look down on women.

The fact that Qing's apparent age kept getting younger due to continuous legal plastic surgery also played a part in this judgment.

She had an appearance that could pass for twenty if she insisted on it.

From Qing's perspective, well, isn't younger better when it comes to age?

Could you be sad because you're young?

That was something only those with low status would say.

"…? Then aren't you a year younger than Xian Gege? Why are you called Sister?"

"Ah, Zhugeie is only twenty-one? He's just big in size, but he's a complete baby, huh? Originally, when I met your brother, I guess I was about twenty-two? Something like that?"

"…? Does Sister age backwards?"

It was a cute disaster brought about by innocence.

"Didn't you just almost say something dangerous?"

"Ah. I'm sorryyy."

"Alright. I'll let it slide because you're cute."

"But then, if Sister uses her Inner Qi too, aren't you an incredibly powerful Master?"

"Didn't I already say? This body is a master. A body on the verge of the Transcendent Realm, a veteran of a hundred battles who has defeated countless Transcendent Realm Masters with the combination of Inner and Outer Arts. Ah, I'm not a veteran, huh? A young veteran, hmm, young veteran doesn't sound right. Then a great… hmm, I want to eat some intestines…"

Qing activated her specialty of ‘thinking everything that comes out of her mouth is valid speech'.

At this, Zhuge Xiang burst into clear laughter.

"Oh, then, can't Xiang be the principal wife instead of a concubine?"

"Tut-tut. Don't you know the saying that fortune has no back of the head? It's too late to reach out after it's passed."

"Hmph…"

"Later, when you grow up and become very pretty, maybe when you become one of the Five Great Beauties like the Thunder Flower or the Scheming Flower or the Vile Flower, then I'll accept you."

"…Isn't it usually the Wisdom Flower or the Virtuous Flower or the Intelligent Flower?"

"What, can't I attach good names too? The really ugly-looking one next to me is the Poison Flower, you know?"

"Ah, right! But then, what about Sister? I've never heard of the Herculean Flower or the Xiang Ji Flower…"

As the two chatted like this and disappeared, a huge shadow fell over the empty space.

A shadow fell over the iron ball in an ambiguous state, neither firmly embedded in the ground nor completely free.

It was because some senseless human had left without cleaning up after use.

Perhaps because of this, there were huge hands carefully grasping the handles with both hands.

"Hup."

With a breath-catching sound, a modestly dug hole in the ground was revealed.

The ground had not fully thawed as spring had just arrived, so this was about right for a 250-catty iron ball falling.

The iron ball was lifted with difficulty and quietly placed back in its original position.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When she returned to the guest room and showed her arm, Tang Lan-Ah scolded her, saying she had really done a number on herself.

She asked what on earth Qing had done in the middle of the night to properly damage her ligaments like this.

But listening to Tang Lan-Ah's explanation, the ligaments had stretched so much that the gripping parts were already loose and lost elasticity, and some had ruptured, so she should avoid using her shoulder altogether and not even think about lifting her arm for a while.

Only then did Qing regret her attitude towards Zhuge Xiang the night before.

It was truly a foolish act.

"But why is it only like this on top? The lower part is fine?"

"Is that strange?"

"Of course, the upper arm with more muscle is naturally stronger and more stable, isn't it? The muscles in the forearm are just for bending and rotating the wrist, so they're inherently weaker."

Of course, it was thanks to the White Hand Demonic Arts.

The White Hand Demonic Arts protected the area below the elbow like a vajra body, so even in the pathetic show of strength in the middle of the night, it had faithfully protected its stupid owner.

"Let's apply some acupuncture first. It would be good if we had ice. Since this is the Zhuge Clan, they must have ice, right?"

"It's okay. I can use Ice Arts."

"Huh? Ice Arts? How?"

"Well… I just can?"

"That's great. Can you freeze this a bit? Not too much."

Tang Lan-Ah handed Qing a towel soaked with water.

As she drew up her True Qi as if cooling Longjing tea, frost immediately began to form and freeze.

"Ah. That's enough. That should do."

Tang Lan-Ah rubbed the towel to loosen it up, then wrapped it with another towel and tied it to Qing's shoulder.

"Tell me when the towel gets mushy. We'll need to untie it, freeze it again, and retie it."

"Can't we just freeze it like this?"

"With ice touching bare skin? That would cause frostbite."

"Ohhh, that's a proper physician's answer. You're cool at times like this. But didn't you say you'd apply acupuncture? Can you do that with it wrapped like this?"

"Ah. Right."

Tang Lan-Ah quickly unwrapped the towel.

Qing's eyes narrowed.

\textit{The 'cool' comment should probably be retracted.}
