\chapter{Journey to Kaifeng (2)}

Gramps, whom Qing hadn't seen in a while, was worried sick.

"Above all, take care of yourself. I have prepared some modest travel expenses, so make sure you never go hungry."

As he said this, he handed over a money pouch. When Qing opened it to check, it was full of bright yellow gold.

"Wow. If this is modest, how much would be immodest? I'll use it well. Thank you."

"This much is modest for you. Always get the best room and buy the most expensive dishes. Being lavish is how you avoid being looked down upon. Do not bother being diligent on your trip. Sleep when you want to sleep and play when you want to play."

Usually people say the opposite, but…

It was convincing since he was saying this while handing over a pile of gold.

And he even added on more of the legendary Power of Convincing!

"These are promissory notes I prepared just in case. Each is worth one gwan of gold, so do not even think about saving money."

"Wait, Gramps, where did you earn all this money?"

"It is the operating funds for the trading company."

It was a bold declaration of embezzlement.

"Oing. Is it okay to give that to me?"

"When a business really gets going, excessive money starts gushing out from somewhere. Even if it goes bankrupt, it is the business that goes bankrupt, not me."

"Ooh. You've really become a proper business owner."

When they were in Sichuan, even Cui Liweng didn't know how the Divine Cult would respond.

But now he knew, so the Divine Cult's assets were essentially Qing's assets.

Cui Liweng then went on to nag.

"If you get into any unnecessary trouble, do not leave them be, but deal with them cleanly to nip any problems in the bud. Also, be careful of men who act overly friendly for no reason. If necessary, you can accuse them of being sex fiends and deal with them without consequences."

"Come on, Gramps, am I a child? I know all that already."

"I would like to go with you if I could, but Senior is right. An old man tagging along would only be a burden to you."

"Honestly, I don't really care. As long as Gramps takes care of his own grudges, that's fine. If Gramps wants to come along, you can just come."

Cui Liweng smiled contentedly at this.

"It is not like I will have to endure forever, and it will naturally be resolved with time. There is no need for an old man to act like a child with a stomachache. Do not worry about this old man and just enjoy yourself."

"Who's worried about Gramps? If I worried about a Master, they'd just say ‘Take care of yourself first'."

Only then did Jian Buxi return.

She said she had already packed for the trip to Kaifeng and immediately came out with her luggage, so there was no reason to delay further.

"Ah. But didn't you say to live in hiding? Isn't the Xue Clan Trading Company a bit too eye-catching? Is Xue a common surname?"

"I thought about it, and I realized there's no need to hide when I haven't committed any crimes."

For reference, Xue Ganom originally belonged to a branch sect of the Northern Sea Ice Palace, and after turning it into a sea of blood regardless of masters, seniors, peers, or juniors, he burned down the building, stole the secret manuals, and left.

However, from Xue Ganom's perspective, it was just justified revenge, even if his methods were a bit excessive.

He had only hidden because he was afraid of the Ice Palace's trackers, but now that he had strong backing, he intended to live life to the fullest.

Qing had roughly assumed that Xue Ganom had just killed a few people who bullied him and ran away, but she didn't know that he had burned everything down to the roots.

"You thought well. It would be a loss for all of Wulin if the neighborhood's top intellect was stuck in a corner."

"I've been thinking about this for a while, but isn't ‘neighborhood's best' a bit ambiguous?"

"What, are you looking down on the neighborhood? And are you asking me to gild your face with your own words? The Xue Clan Trading Company is still at the neighborhood level, so raise it well."

And then Qing waved goodbye noisily.

Cui Liweng, who saw her off, patted Xue Ganom's side and spoke.

"Well, let us go. If you want to be recognized as a greater strategist, you need to grow the trading company, right? Now that it has come to this, you should aim to become Zhongyuan's top intellect."

"Yes, Elder."

Then Xue Ganom suddenly recalled.

\textit{But wait, since when and why did I start being evaluated for my brain?}

Xue Ganom was someone who had never once thought of himself as smart.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

First, they had to take a boat to Muhan.

On the way to the port, Jian Buxi spoke blankly.

"You know, I just realized I've never been on a boat before. Hehe. I'm excited. Are we going on a big boat? I've only seen a boat this big before."

Jian Buxi spread her arms wide up and down as she spoke.

At this, Tang Lan-Ah's eyes lit up beside her.

"What? You've never been on a boat? Then you probably don't know that you have to take off your shoes when you get on a boat, right?"

"Huh? Why would you take off your shoes? Then your feet would get all wet, wouldn't they? I might be an ignorant woman, but I won't fall for such stupid talk. Come on, even a seven-year-old wouldn't fall for that kind of joke."

"Huh? Is it, is it that obvious?"

"Of course. You can just look around and see if anyone else is taking off their shoes. Have you ever seen anyone do that, Sworn Sister's friend?"

"Uh… That's true…"

Tang Lan-Ah nodded with a sour expression.

"But why are you glancing around like that, Sworn Sister's friend? Is there something interesting- Wow, look at what she's got stuffed in her chest."

"I-I didn't, okay!? I wasn't stealing glances at her che, huh? But what did she have stuffed in there?"

"The shape is just like that, you know?"

"I'm not sure…"

Qing let out a deep sigh.

When there are two idiots, there's always one that's even more of an idiot than the other.

\textit{Sworn Sister Wannabe has already taken this round, but, um, is it okay for a physician to be like this?}

\textit{Is Zhongyuan medical community going to be alright like this?}

Bickering like this, they arrived at the port, and both country bumpkins were in a frenzy, gawking with their mouths wide open.

Then Tang Lan-Ah finally showed a splendid side befitting a rich family's daughter.

"Hey, let's ride that one. It looks the biggest and most luxurious. I'll pay for the fare."

"Oing? Why do you have to pay to ride a boat?"

"You, are you making fun of me again? Do you think they'll just let us on for free?"

"It's different for everyone."

Qing grinned, planted both feet firmly on the ground, and raised her hand high.

"Everyone! I have a Dragon King's Plaque here! I'm looking for just one ship owner who wants to legally evade taxes to Muhan!"

Legal tax evasion!

It was like a dream come true for all merchants in Zhongyuan.

The Chinese people, while hating taxes, surprisingly didn't like illegal tax evasion.

This spirit continued to Qing's modern homeworld, where Chinese people absolutely did not engage in illegal tax evasion.

After all, if caught, it undoubtedly meant execution (purging).

Above all, legal tax reduction was possible.

Since they didn't know where their taxes were going anyway, instead of paying taxes to the country, they offered them to high-ranking Party members, receiving massive tax exemption benefits along with accumulation of guanxi.

It was a different culture from Koreans, who considered those who paid a lot of taxes to be the world's idiots, morons, and imbeciles, and would praise without reserve, letting the whole nation know as if it were a holy anecdote from mythology; just for the mere act of a rich person properly paying the legally stipulated taxes.

Anyway, there was fierce competition to host the precious guest.

Finally, the owner of a seven-story Dragon Palace-like ship humbly bowed at the waist and won the honor of entertaining the distinguished guest…

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

For these reasons, Qing received truly exceptional treatment.

They cancelled the reservation for the best cabin, paying ten times the cancellation fee to return it, and generously provided expensive alcohol and costly dishes, to the point where it was hard to tell if they were inside a ship or in paradise.

In reality, the money spent on entertaining Qing ended up being three or four times more than the taxes they would have paid.

However, would a wealthy ship owner who owned a seven-story large ship have made such a fuss just to avoid some taxes?

It was because they wanted to get back at those annoying Waterway Forts bastards who block the waterways with harpoons and extort money without doing any real work.

"Stop!"

"You stop! We have a guest with the Dragon King's Plaque on board. Do you dare to cause trouble?"

"Please proceed!"

The Waterway Forts personnel immediately tucked their tails and retreated.

It was the most satisfying moment in the ship owner's thirty-year career.

The ship owner was happy, Qing was happy, and even the guest whose reservation was cancelled made money by receiving ten times the deposit, so it was a happy conclusion for everyone.

As for the Waterway Forts, the Dragon King's Plaque was originally given out for situations like this, so this was all part of treating their benefactor well.

And so, as they ate well, played well, and slept well, before they knew it, the ship flowed along and arrived in Muhan.

Muhan is not the name of a city, but a term combining three quays meaning 'Three Ports of Muhan'.

Among the famous places, there was a restaurant called Yellow Crane Tower, said to have been built by Sun Quan (that very Sun Quan) himself.

Originally used as a watchtower, it burned down and was rebuilt several times, gradually becoming taller, and by the Tang Dynasty, it had become a skyscraper that was always mentioned when discussing the greatest towers under heaven.

At the top, they hung a huge plaque engraved with 'Piercing the Sky and Reaching the Clouds', which also grew slightly larger each time the original, which had burned and disappeared, was remade.

The original was a phrase written by Sun Quan himself.

It meant 'I will finally confirm with my own eyes the sky of Chu', and was highly regarded as a phrase of lofty spirit, comparing himself to Xiang Yu, the Hegemon-King of Western Chu.

It might seem a bit grandiose for the chieftain of a primitive tribe whose specialty was dying young while shouting about their liver after eating raw freshwater fish, but still.

There weren't any particular specialties besides that, but in the distant future, it was destined to become famous as the hometown of a dangerous disease that would strike the entire world.\footnote{COVID-19}

What was this place called in the modern era? Well, Muhan is read as 'Wuhan' in a certain uncivilized language.

And if the Heavenly Slaughtering Star had known this, it might have abandoned its obsession with a mere human girl and embraced this city instead.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At any rate, with a full moneybag and Tang Lan-Ah by her side who could splurge if necessary, Qing had nothing to fear anymore.

How could they just pass by when that golden roof that had been visible in the distance since they were on the boat was said to be one of the most famous restaurants in the world?

As soon as they got off the boat, they headed straight for it, determined to either make a reservation or pay extra to have a meal if possible.

However, the Yellow Crane Tower was a famous landmark known throughout all under the heavens.

"If you want to make a reservation, it would be four months from now…"

"Four months?"

"Or maybe ten months. Spring and autumn are already fully booked without a single day free."

"Ah…"

\textit{Well, there's nothing we can do about that.}

Qing was surprisingly a person of common sense who treated common sense with common sense.

Qing drooped her shoulders and clicked her tongue in disappointment, taking in the high scenery of the Yellow Crane Tower once more.

Then suddenly, something caught her eye.

A man leaning against the railing on the highest sixth floor, looking outside.

A grin spread across Qing's face behind her face veil.

\textit{Oooh. If there's someone I know, wouldn't it be okay to join them?}
