\chapter{Journey to Kaifeng (7)}

If you're going to stay for a day anyway, it's better with a familiar face.

And during the last visit, the Daijing Sect Leader's snack selection was quite remarkable.

So Qing was about to make her choice when…

"Since this is my first time traveling in Jianghu, I would like to have many experiences if possible. Staying at an inn is one of them."

Tang Lan-Ah conveyed a roundabout refusal.

That's how it sounded to Qing.

For reference, the 'I' she used was a choice of formal vocabulary that elevated herself one level above 'this girl'.

While it was a roundabout refusal, it was also a firm attitude indicating she would not accept any objections.

"Ah. Then it can't be helped. Then, may I at least treat you to a meal…?"

"Our travel expenses are sufficient enough that we don't need to impose."

"I see…"

Wang Xunxi and the other martial officials who had come to greet them drooped their shoulders.

Thinking, as expected of one of the Five Flowers of Wulin, what a haughty attitude.

Qing thought there was no need for all this, but since it wasn't a solo trip, she had to accommodate her companions.

After staring at Tang Lan-Ah until the end, they then left the men who seemed to think the carriage would become transparent if they stared hard enough, and found an inn.

"But, why? Wouldn't it be nice to stay for a day?"

"Come on. Where in the world is anything free? They're probably all planning to go to the Wulin Conference anyway, so it's annoying if they subtly want to travel together."

"Is that so?"

"Sister Tang, how could that be? With three ladies such as yourselves, how could any man dare to ask to travel together?"

In fact, asking to travel together on a journey of women moving together becomes an unofficial discourtesy.

Is a detailed explanation even needed?

Even when transcending eras, it was the kind of behavior that would make people curse, saying "That bastard is crazy about that woman."

"Oing?"

At this, Qing looked at Zhuge Lixian.

With a look that said, 'Who said they wanted to go together?'

"Ah. Sister, you're indifferent to Zhongyuan affairs. I'm a Zhuge, aren't I?"

The choice of words, not saying she was ignorant, well reflected Zhuge Lixian's character.

It was also an answer with multiple meanings.

In a good sense, since the Zhuge family's aesthetic standards were well known, even if he asked to travel together, it wouldn't be taken as a come-on.

In another sense, it meant that someone of the Zhuge Clan's status had no reason to make advances in such a way.

Moreover, with a Daoist elder, the elder's sworn sister, and Tang Lan-Ah, the precious daughter of the Tang Clan, it was even natural for the Zhuge Clan to be together - this was how the top echelons of Zhongyuan interacted with each other.

"Then isn't it hard to bring up traveling together even if we stay overnight? Is there really a need to be so cautious?"

"Oh my, Sister. You should know the danger of your beauty. Even if they ask to travel together, we don't particularly have a reason to refuse, so if they say they'll endure the shame, wouldn't they just bring it up?"

Then Tang Lan-Ah added a word.

"That's right. Qing'er, you need to know how pretty you are."

"Hmm. It's not that much."

At any rate, it was around early evening.

People in Zhongyuan eat a very light breakfast and lunch, but have a very hearty dinner.

Although the farmers, who make up the absolute majority of the population, might not agree, farmers were considered somewhere between humans and livestock, so they weren't counted as people of Zhongyuan.

Of course, Qing ate hearty meals three times a day, but still, she put the most effort into dinner among them.

This was because there were many dishes that could only be ordered in the evening, as they were made in large quantities for sale.

There was also the advantage that if she got acupuncture before bed, the paralysis would wear off around lunchtime, so she could eat dinner by herself again.

After all, it was a bit frustrating that the two of them fed her only after she had completely swallowed.

So after dinner, they took a walk around Nanyang Lake to aid digestion, played a bit, got acupuncture, and went to sleep.

It wasn't a diary so it wasn't written down anywhere, but it could be said it was fairly enjoyable.

And then she received a bath, got acupuncture while lying down, and then fell asleep leaning on Sworn Sister Wannabe in the best room, which was like a normal day.

These days, she shared the same bed every day, feeling sorry for constantly refusing when Jian Buxi asked to share a room before, not knowing Zhongyuan culture.

When she was at the Zhuge Clan, she asked Zhuge Lixian if she might be misunderstanding something, and his answer was firm.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the past, roughly a week ago.

Zhuge Lixian, the top intellect among muscle men, said:

"For sworn sisters, isn't it a touching display of affection to use one bed, share one blanket, and sleep embracing each other?"

"Touching display?"

"That's right. In the past, didn't the three great heroes Liu Xuande, Guan Yunchang\footnote{courtesy name of Guan Yu}, and Zhang Yide\footnote{courtey name of Zhang Fei} also share one bed, embracing each other and sharing warmth, and weren't they praised as the most affectionate brothers under heaven?"

What's the point of sleeping far apart on the same bed?

True affection is formed when you have to endure cold times with each other's body heat on a cheap bed barely big enough for a booger, with a cheap blanket that doesn't provide warmth.

"Huh? Those three?"

"So when Liu Xuande brought Zhao Zilong\footnote{courtesy name of Zhao Yun} into his bed, Zhao Zilong was moved to tears and served him with lifelong loyalty, and even in Ancestor Zhuge Liang's diary, he recorded the emotion of when General Liu first offered to share his bed."

These are examples of Liu Bei using bed-sharing politically.

"Uh. Hmm. I see."

\textit{This is quite eye-opening.}

\textit{Is this the reality of the Three Kingdoms?}

\textit{Is it because it's a different world?}

\textit{Surely it wasn't like this in my original home world, right?}

"In contrast, a fellow named Cao Mengde\footnote{Cao Cao's} didn't share a bed even with his cousin, so Liu Xuande, in comparison, had a tendency to particularly invite his subordinates to his bed to spread his name for benevolence and righteousness throughout the world."

"Your choice of words is a bit strange."

Of course, purely, without any unsavory incidents, they just slept close together on one bed, just literally as stated.

But for someone with a more modern sensibility…

\textit{Ugh, uuugh.}

"There's even a saying that if Cao Mengde had shared a bed with Sima Yi even once, the owner of the world might not have changed."

"Cao Cao lost because he didn't sleep with Sima Yi?"

\textit{Hm? Did Cao Cao lose?}

\textit{Wasn't he killed when Hua Tuo cracked his head?}

Her knowledge of the Three Kingdoms was roughly at this level, skimmed through manhwa.

Qing only knew the names of famous people, knowing it at a level that almost rewrote history.

"If an adult shared a bed with his father, it would be almost equivalent to an adoptive father, so how could they dare to tease and mock?"

Cao Cao might feel a bit wronged, as his family was basically wealthy, so they never had times difficult and poor enough to overcome with one bed.

This contrasted with how the Three Sworn Brothers still slept together when they gathered even after Liu Bei established himself in Shu.

However, Liu Bei was married, it was difficult for the three brothers to gather after he established himself, and all three were heavy drinkers who lived and died by alcohol, so they would drink in the room and pass out, going straight to bed.

Qing also had many memories of rushing out in department groups during university, drinking heavily, and then being neatly packed into inn rooms for group sleep.

However, he only said that it was a touching display of affection to sleep embracing each other under one blanket.

This meant that people didn't actually do this.

They wouldn't call something everyone does a touching display.

Zhuge Lixian nevertheless explained with particular emphasis.

It wasn't to tease Qing.

There was just a small misunderstanding.

Rather, Zhuge Lixian, interpreting it as that kind heart trying to build up the sworn sisters' spirit, ended up admiring it.

As if saying, 'she's not my servant, she's my sworn sister, so don't treat her carelessly'.

So Zhuge Lixian had indirectly expressed that he would now properly recognize her as Sister and serve her, so please stop now.

However, this was too high-level an expression for Qing to understand, so she just took it literally and thought, "Is this a cultural difference?"

There was also the shock of learning Liu Xuande's true nature.

In fact, his only truly close friends in the world were his two sworn brothers, and he was a gloomy big-eared guy who pretended to be a sage-like ruler with a political performance of his utmost sincerity.

Of course, one might say that Liu, who at least tried to act like a good person even with a black heart, was much better than Cao, who was born without guilt due to a genetic disease and had a social development disorder.

Moreover, Cao's lack of guilt and empathy was passed down genetically.

Sima Yi, who cut off that line, could be called the true chivalrous hero under heaven.

Plus the achievement of finely shredding the Chinese people into the Sixteen Kingdoms!

He was truly a saint who would live happily ever after, receiving blessings forever next to the highest throne in heaven.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And back to the present.

Qing's group, who had rested well for a night in Xinyang, started their journey north towards Kaifeng again.

Passing through small towns and villages, finally, what was bound to happen eventually happened.

"Ah."

It was Tang Lan-Ah, who had developed some skill and was changing angles while applying acupuncture.

However, this was one of the taboos of acupuncture.

"Are you going to keep making ominous exclamations while doing acupuncture?"

"My long needle…"

This is exactly the kind of action that's perfect for breaking needles.

This was why needles should be inserted perpendicular to the affected area, without force, gently tapping them in.

However, she had gripped the needle with her fist, shaking it around and stabbing it in roughly, so how could a thin, long needle possibly withstand that?

Tang Lan-Ah made a tearful face.

It was both because a familiar tool she had used for a long time had broken, and because the needle Tang Lan-Ah used was no ordinary needle.

It was a masterpiece among masterpieces, a luxury item among luxury items, that a famous needle craftsman had prided as his life's work.

The fact that it had withstood Tang Lan-Ah's crude acupuncture technique, inserted with her whole body's strength until now, was proof that it was truly a world-class luxury item.

As Tang Lan-Ah was blankly staring at the broken long needle, that's when it happened.

Qing, feeling a bit of conscience, knowing it wasn't the time to bring this up but still having a question she ultimately had to ask.

"Um… where's the remaining part?"

"Huh? Uh… huh?"

It was a talent to make someone nervous with just one syllable.

"Can it be pulled out?"

"If, if you move your arm like this, like this, it should naturally come out."

"My arm doesn't move, though?"

"Well. My dad will come to Kaifeng too, so we can ask my dad to…"

"What?"

"Well, why don't you think positively? Since you won't be using any strength in your arm at all, in a week the injury should be all healed…"

And so, after this very minor incident where her arm became completely paralyzed - according to the medical opinion of Tang Lan-Ah, an authority in traditional medicine - the group arrived at a large city.

Its name was Zhumadian.

"Zhumadian was also a land called Runan in the past. The current Runan has been separated into Runan County to the east, which happened during the Tang Dynasty…"

An unsolicited explanation automatically popped out.

Of course, it was a sound that dispersed emptily as no one in the group was properly listening.

Still, Qing found it amazing to see how he always burst into speech like this.

\textit{Is there some book that just collects information like this?}

\textit{How does he string it all together so smoothly?}

Of course, among them, she did pick out interesting stories with uncanny accuracy.

For example, the story of how Zhumadian got its name because of Yang Guifei, one of the Four Great Beauties of China and famous as the greatest villainess under heaven.

Yang Guifei loved lychee the most among fruits, but it happened to be a fruit from Southeast Asia.

This city was where they stopped once while quickly transporting it, hence it became Zhumadian (literally meaning "stop point for horses").

In fact, it's not something to laugh off.

There was even a saying that one of the reasons for the Tang Dynasty's downfall was the enormous cost spent on the 'lychee transport operation' to bring fresh fruit for Yang Guifei.

For reference, lychee is called 'lizhi' in Chinese, and in the history of Qing's homeland, the Westerners took lizhi and named it 'lychee' due to pronunciation limitations.

It was that lychee that was always piled up like mountains as dessert in cheap all-you-can-eat places.

However, its place of origin was Southeast Asia, so it originally had a different name.

But no one in the world, not a single person in past or future, was ever curious about the original name of the Southeast Asian fruit,

So that name remained unknown, they say.

After hearing this interesting explanation, Qing thought.

\textit{Ah. Lychee. Lychee is delicious too. I want to eat lychee.}

However, since Qing was not Yang Guifei, no one would go get it for her just because she wanted to eat it.

Instead, there was one girl being annoying about something else.

"Qing'er, let's go look for needles."

"We haven't even unpacked yet…"

"We have to go before the sun sets. The needle craftsmen close their metal shops and go home when it gets dark…"

They hadn't even found an inn or unpacked their luggage yet, but Tang Lan-Ah was suddenly urging to go look for new long needles.

She said if they were lucky, they might be able to pull out the needle stuck in her shoulder with the iron tongs used by needle craftsmen.