\chapter{Journey to Kaifeng (4)}

In fact, Qing, being from Hubei, knew Hubei cuisine inside out.

When it comes to Hubei, it was first, golden mandarin fish, and then soft-shelled turtle.

Roughly speaking, in Chinese people's perception, if you put mandarin fish or soft-shelled turtle with lotus root and cook it, they would generally accept it as Hubei cuisine.

There were also lamb and duck dishes.

But those two were so common in Chinese people's daily lives that they were enjoyed in any region, and pork was just like China itself.

The Chinese love for pork went beyond just eating it; they even came to resemble its national character, so one could say they were practically living piglets.

Besides these, various freshwater fish dishes were developed, but interestingly, they don't often eat them as sashimi.

Of course, it's not that they don't eat it at all.

This aversion was due to records of geniuses from the ancient State of Wu dying young after being defeated by parasites from eating raw freshwater fish.\footnote{It's actually Chen Deng of Wei}

And then they all blamed the heavens for it.

From heaven's perspective, these people ate parasite-ridden things claiming they were delicious and died, but before dying, they cried out 'Oh Heaven!!' while coughing up blood, so heaven probably didn't feel any affection for the State of Wu out of spite.

So the dishes that Zhuge Lixian laid out until the table legs nearly broke were actually all familiar to Qing.

However, unfamiliar dishes bring a different kind of joy, and familiar dishes are often more delicious.

After a long time (three shichen), Qing started a storm-like meal with a serious attitude.

In fact, the Chinese strangely love carp family friends when it comes to freshwater fish.

However, these friends are structurally like monsters with bones spreading in all directions, making them difficult to eat.

But Jian Buxi, sitting beside her, somehow skillfully deboned them and kept piling them on Qing's plate.

Not wanting to lose, Qing kept clearing her plate quickly.

"What? I, I can too."

Tang Lan-Ah clumsily deboned and occasionally placed ragged pieces of fish on Qing's plate.

"Thanks, but there are still bones in it, you know."

She said this while chewing the sharp freshwater fish bones along with the meat.

Tang Lan-Ah also tried to debone the fish, but as mentioned earlier, these elastic and sharp-boned fish with bones spread everywhere without a single empty spot were truly the worst of the worst, the emperor of evil among evils.

Only after Tang Lan-Ah put the fish meat she had deboned into her mouth, found it half meat and half bones, and spat it out unable to chew, did she realize how serious it was.

"Oh? Sorry, this has so many bones…"

"It's okay. It's delicious. Originally, if you chew the bones slowly, they have a savory taste."

"Even so, give it here, I'll do it again."

"I said it's fine. You went to the trouble of deboning it for me."

Qing said this while shoving into her mouth the ragged pieces that Tang Lan-Ah was trying to take back.

"You…"

For Tang Lan-Ah, it was something absolutely inedible that she had to spit out.

But seeing her forcibly(?) eat it, what woman wouldn't be moved?

However, Qing was just eating.

She already had a body that could crunch and chew even tough rib bones, let alone fish bones.

This is the greatest reward of having high stats.

"If it's hard, debone the mandarin fish instead of the carp. It doesn't have many bones."

"Huh? Mandarin fish? Which one is that?"

"That one."

‘Jigeo' meant carp, and ‘gweoleo' meant mandarin fish.

However, to Tang Lan-Ah, all fish looked the same with their fish heads.

For Tang Lan-Ah, fish always came delivered to her with their names.

In the style of 'Dear, the croaker is really delicious'.

So this was the first time in her life that she actually deboned a fish for someone else, and if the Tang Clan Lord and his wife had seen this, they would have lamented that raising a daughter was all in vain.

"Haha. Sister, you eat so heartily!"

"You're not insulting me, are you?"

"How could I! It's just like the spirit of Sister Peng in her prime, at this rate, this little brother might end up falling for you. The women of Zhongyuan all pretend to eat daintily, which rather makes one lose their appetite when dining together."

"Ah. Young Lady Peng did eat well too. Though she was a bit of a picky eater."

"Does Sister Peng still only eat meat?"

"Yeah. She says you have to eat muscle to grow muscle."

"Like cures like is just a superstition, but thinking of Sister Peng, it doesn't seem entirely false. Ah, like cures like means eating the same thing to…"

Zhuge Lixian showed off his miraculous chatter, speaking without slurring at all even while eating everything.

Qing pretended to listen to the story while focusing on her meal, since he was a friend who bought her food after all.

Ah. Oh. Yeah. Hmm. I see. Right.

The enjoyable mealtime passed with these soulless responses.

"Wow, that was a good meal."

Qing had already loosened her belt while eating earlier, so she gently rubbed her protruding belly.

Tang Lan-Ah poked it and exclaimed in admiration.

"Wow, it's really firm. To think you ate all that…"

"Actually, I could eat more. But that space is reserved for dessert."

"No, how do you eat like this every meal and not gain weight. Hmm. All the flesh goes up to the flesh lumps…"

As Tang Lan-Ah's hand started to rise sneakily, Qing slapped it away.

"There you go again."

"No, I did it without thinking."

Qing narrowed her eyes.

\textit{It's fortunate she was born a woman.}

\textit{If she had been a man, wouldn't she have become the world's greatest lecher and scoundrel?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In fact, the consensus among Jianghu people was that Wuhan itself didn't have much to see.

At best, there was only the Yellow Crane Tower skyscraper on high ground, and Donghu Lake, famous for its cherry blossoms, was now out of season and just a quiet lake where you could view the horizon.

Of course, being able to see the horizon from a lake could be considered the spirit of Zhongyuan, but still.

Yingchun Temple was famous, but not quite a tourist attraction like the White Horse Temple in Luoyang, so it was just a temple people visited when going to Donghu Lake.

So with nowhere to go after dinner, they decided to stop by the Zhuge Clan and stay for a night.

Although he talked a bit much, Zhuge Lixian was an enormous little brother who was inherently friendly and had some cool aspects.

There was no reason to refuse when he said they could stay at his house for a night, and since they were going to Kaifeng anyway, he wanted to go together.

In fact, there was a hidden attraction in Wuhan: the short street leading to the front gate of the Zhuge Clan.

It was filled with tea houses and restaurants, with many tables set up outdoors, each occupied by burly older sisters and occasionally men.

The businesses here were owned by the Zhuge Clan, and the customers were those who gathered hoping to catch the eye of the Zhuge family members, so it could be said they had a devilish sense for making money.

-What's with those scrawny wenches? Do they think they can wag their tails just because their faces are somewhat decent?

-I know, right? Those girls with waists thinner than your arm daring to cling to the young master.

-Look at their faces. They're smaller than my fist.

-They're not womanly at all. A proper woman should compete with muscles.

The content Qing overheard when she focused on their whispering was quite alarming.

\textit{What's this?}

\textit{Are these people from some distant ocean women's country?}

\textit{What do you do competing with muscles? Is this some kind of abduction marriage?}

\textit{Is this that famous gender reversal thing?}

Of course, Qing didn't know anything about Hearing Technique (Inner Qi-enhanced hearing).

She was just a superhuman who had transcended human limits even in hearing, so she could hear everything if she concentrated.

It wasn't that they were speaking loudly enough to be heard; it was just that the content of their whispers to each other was shocking.

Since there was no particular reason to feel bad about it, Qing pretended not to have heard.

When visiting a friend's house, the proper order was to first greet the parents.

Before that, they were on their way to unpack their luggage.

"Hyeon Gegeee."

Qing flinched.

\textit{Gege?!}

\textit{Who would use such an outrageous word!}

\textit{And even stretching out the end of the word!}

However, at the same time, a tiny thing came running, a girl who looked to be about six or seven years old.

\textit{Ah, for a little kid, it's acceptable.}

\textit{How cute.}

"Oh, A-Xiang. Were you playing nicely?"

Zhuge Lixian lifted the girl high above his head, spun around about four times, and then neatly sat her on his shoulder.

Usually, one would give a piggyback ride, but his shoulders were so broad that he could seat her there.

The clear laughter characteristic of children filled the surroundings.

Qing smiled a fatherly smile behind her face veil.

It was a heartwarming scene to see, after all.

This was Zhuge Xiang\footnote{諸葛香. Jaegal Hyang(제갈향) in the original text}, the youngest direct descendant of the Zhuge family.

However, the following conversation was a bit strange.

"I wonder what book Xiang read today?"

"Um, today, Hyang read thirty-one chapters of Wuliuzi."

"Oh, Wuliuzi! That's a good book. Yes, it's quite an interesting book too. Which part left the deepest impression on you?"

"Um, starting with the Heavenly Officials, since it says that the weather is just a matter for the Heavenly Officials and doesn't include it in personnel matters, this is a different perspective from Sun Tzu's timing, terrain, and…"

"Oh my. That's just emphasizing the importance of preparedness before the Heavenly Officials, it's not that Wu Liao…"

"But after the defense, if you dig water channels, dig wells and expand warehouses in preparation for raids, and prepare for winter in case of drought…"

"Those are all pre-war preparations that should naturally be…"

Qing looked at Tang Lan-Ah.

To see if she understood what they were saying.

As Tang Lan-Ah was also looking at Qing with the same expression, they both just thought, 'Well, I guess that's how it is'.

Of course, there was no need to check with Jian Buxi separately, so neither of them particularly glanced in that direction.

Feeling somewhat like idiots, they uncomfortably unpacked their luggage and then paid their respects to the thin Zhuge Clan Lord and his burly wives.

"Please take care of our A-Xian. The child's head is only full of knowledge, so he's still naive about worldly matters. I hope you'll cherish him like a younger sibling."

"Yes, Elder."

"Right. Ahem. Young friends should play together."

Despite his most beloved and proud son bringing along a group of women and even declaring he would leave with them, he maintained a plain attitude without any unnecessary comments, as if he had brought along some same-sex friends.

Rather, the one who looked upset was Zhuge Xiang, who was clinging tightly to Zhuge Lixian as if she had made a nest in his arms.

"What? Gegeee, where are you going?"

"This child, A-Xiang! Stop being clingy. Let your brother go meet his friends and come here."

"No, I don't want to, Xiang wants to be with Gege. No, I don't want to."

Zhuge Xiang clung tightly, but no matter how much strength a young child might use, with a mother whose arm was about as thick as her daughter, there was no way she could win.

The little one couldn't overcome her mother's strength and was pulled away.

After that, they moved to a separate building, laid out some snacks, and just chatted casually.

Surprisingly, the various stories Zhuge Lixian told were quite interesting.

Then, saying he had to pack his luggage too, he left early, and they also soaked their bodies in a hot bath.

They even allowed Sworn Sister Wannabe to attend to them during the bath.

And then, while sitting on the porch of the guest room, swinging her feet and drying her hair, Qing sensed a gaze.

When she turned her head, there was one head peeking out from behind the wall.

"Hmm? Little one? Your name was Xiang, right?"

"Ugh…"

At Qing's gesture, Zhuge Xiang approached hesitantly and suddenly asked.

"You're the sister who was wearing the face veil earlier, right? Are you going to be our new sister?"

To be precise, she asked if she would become a ‘suja', which was the Chinese word for new sister-in-law.

Qing asked playfully with a smile.

"Why? Don't you like that?"

"No. I don't like it."

"Why don't you like it?"

"Because you're weak."

"Weak? This body is a Master."

Qing emitted Qi with barbaric output from her hand.

If Ximen Surin had seen this, it would have been grounds for a nuclear noogie.

She would have said, 'You have nothing to show so you're showing Demonic Arts to a child?'.

Fortunately, or unfortunately, young Zhuge Xiang didn't have the discernment to recognize the White Hand Demonic Arts.

"Noooo. Not that. You don't have muscles. You're weak."

"But I'm strong, you know? I'm totally like Xiang Ji."

At this, Zhuge Xiang pouted her lips.

"Pfft. Liar. Can you even lift 100 jin with those arms?"

"100 jin? I can lift that with one hand."

"Then how about 200 jin?"

"If I use both hands, that's 200 jin, isn't it?"

"What about 300 jin?"

"I haven't tried, so I'm not sure, but I probably could? If it's just lifting, it shouldn't be too difficult. Swinging it around might be a bit hard though."

"Without using Inner Qi?"

"Without using Inner Qi."

At this, Zhuge Xiang slapped Qing's knee.

"You can't, you're a total liar."

"Look at this? Such a tiny thing already trying to win with agitation and fabrication? Haiya, I can't just show you by lifting something directly."

Then Zhuge Xiang answered as if she had been waiting for this.

In fact, she had been waiting.

As a descendant of the Zhuge family, she should be able to devise strategies at the age of seven.

"Then show me."

"Oing?"

"Quickly. Otherwise, I'll tell Gege that you told a bunch of lies."
