\chapter{Journey to Kaifeng (1)}

Chen Changming is a blunt girl without cutesy.

This is because cutesy is something closer to learned behavior than innate.

One needs to accumulate experiences of getting what they want by acting cute as a child to be able to use it as a functional skill when needed as an adult.

Chen Changming had suffered from Meridian Blockage since childhood.

Having watched her family's fortunes decline in real-time because of her, she only knew how to endure and bear it.

She had never even thought of trying to be forceful by putting on airs and acting coy.

"I'm going to sleep over."

"As I've said many times, the law is strict…"

"There's no such law."

"There is in my universe, you know? Come on. It's bedtime for the little one. Your already small height won't grow any more otherwise."

"C-Changming'er is going to sleep over."

At this, Qing opened her eyes wide.

\textit{What? This little brat dares to refer to herself in third person?}

Of course, she and Changming often engaged in trading jokes.

But even the most outrageous things were usually just dry wordplay delivered with that characteristic blank expression.

But right now, Chen Changming herself had her face flushed red with embarrassment.

Qing looked at that red face and finally smiled awkwardly as if she had no choice.

Using age as an excuse to keep a distance especially from Changming, how hurt must she be to act cute when she never did before.

Oh, oh. She looks like she's about to die of embarrassment.

"Alright. It's not like the heavens will punish us for sleeping together for one day, what can we do. But, won't you be cold?"

At this, Chen Changming's eyes widened.

"Uh, did it work?"

"I don't usually forgive someone referring to themselves in third person, but I'll let it slide because you're cute."

For Chen Changming, this was a big step forward.

The realization that sometimes it's okay to act cute.

"Come here."

"Okay."

But, as expected. It's cold!

Chen Changming also had no particular preparation against the winter cold.

Tang Lan-ah's goal was more about wanting to feel that fluffy, weighty softness again rather than Qing herself, so she quickly gave up and ran away in the face of the cold.

However, Chen Changming endured.

The trembling transmitted from the side was concerning, so Qing burst into a mischievous laugh.

"If you're cold, go sleep at your own place."

"N-No, I'm not c-cold."

"Can you stop the sound of your teeth chattering when you speak?"

"I'm n-not c-cold."

Chen Changming answered through gritted teeth.

Qing let out a snort.

"Anyway, you're as stubborn as you are small."

Just as Chen Changming was about to protest, she was suddenly startled by arms wrapping around her. When she opened her eyes wide in surprise, the world suddenly spun dizzily.

Qing had hugged Chen Changming, rolled to the edge of the blanket, grabbed the cloth, and then rolled back to the other side, wrapping them up.

"How is it? A bit better, right? This is how I sleep these days."

Chen Changming froze in an 'Attention!' position against Qing's chest, startled by her pounding heart.

\textit{What just happened?}

\textit{But it's so dark I can't see anything.}

\textit{The blanket tightening around me is stuffy, and all I can do is wiggle my hands and feet a bit, I can't move.}

How long had they been like that?

Qing's voice was heard from above her crown.

"Hmm. This reminds me of the old days. But why are you still the same size, kiddo?"

"Old days? Ah."

Chen Changming suddenly recalled an old memory.

Back then in the tunnel.

Come to think of it, it was just as dark and tight, difficult to move, as it was then.

But there were differences from back then too.

Instead of the smell from not being able to wash, there was just a faint, fragrant scent of Xiangzao (ancient primitive beauty soap).

There was no discomfort of dirt caked all over the body, and no piercing cold seeping through the back and calves.

Her body, which had been stiff with tension, relaxed like a wet towel and leaned against Qing.

It wasn't at all the indescribably strange atmosphere between disciples, sisters, and juniors that Chen Changming had expected.

But it was so comfortable.

It felt like there had never been a time this comfortable before.

In front of her parents, she only felt sorry, so home was always an uncomfortable place with a strong smell of medicine. And while the Divine Maiden Sect family was kind, living in a group without her own room meant she could never fully relax.

"Hey, kiddo. Is life at the Divine Maiden Sect okay? You're not bullying anyone, are you?"

"…? Usually people ask if I'm being bullied."

"Who would bully the youngest of the Second-Grade? The juniors must all adore you. You might bully the Third-Grade kids since you suddenly jumped up the hierarchy, though."

"I don't."

"Is that so? Then that's good."

Qing had seen more than a few disciples hugging Chen Changming to their chest and resting their chin on her crown, so she was just asking casually.

It was like how Korean fathers awkwardly ask 'How's school?' when they're alone with their children for once.

Of course, that's what Qing thought.

Having only had one father, she couldn't know if other fathers did the same.

(Cui Liweng might feel sad if he knew she thought this)

"I wanted to go with you this time."

Chen Changming's voice was regretful.

They had said that when she reached the First-Rate Realm, they would let her go on a short Jianghu trip with Qing, but this time she was rejected.

But it was understandable, as this was an event where all the famous young men from Zhongyuan families would gather.

The scions of prestigious families are fundamentally handsome.

The daughters-in-law of prestigious families learn at least one Fairy Art and are beautiful women, and their children born from them are beautiful, and then the beautiful daughters learn Fairy Arts and become beautiful mothers again…

So after accumulating Fairy Arts through generations of blood, now when one says 'prestigious family', one could tell just from their appearance, thinking 'Ah, how truly noble'.

As such, they couldn't send a defenseless nineteen-year-old girl to such a dangerous place.

"They said next time, didn't they? If there's somewhere nearby you want to go, you should think about it."

"Then, the Northern Sea."

Qing knows the Northern Sea is far, thanks to Xue Ganom.

"If you reach the Peak Realm by the time I get back from this trip."

"Tch. Then Hainan Island. Zhoushan Islands."

"I don't know where those are, but they're islands, right? Are you trying to do a pilgrimage outside Zhongyuan in all directions?"

"Then…"

As they chatted about such trivial things, before they knew it, Chen Changming was making gentle sleeping sounds.

Qing chuckled and accepted the sleepiness she had been forcibly pushing away.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Originally, big events held in Zhongyuan set their dates very, very generously.

This was because guests also came from very, very far away.

Kaifeng, where the Wulin Conference is being held, is located in the northeast of Henan Province, and the Divine Maiden Sect is stuck in the westernmost corner of Hubei Province.

It was not a close distance.

But with Zhongyuan's mindset, it was still close enough to boast that they were neighbors since they were adjacent administrative provinces.

Moreover, the roads are very well-paved.

By taking the Yangtze River to Muhan, then north along the main road through Xinyang, Luohe, Xuchang, then stopping at Zhengzhou, and then turning, it takes just a few days to reach Kaifeng.

These cities have existed since ancient times in the Three Kingdoms period when Liu Bei, Cao Cao, and Sima Yi fought for control of the world.

Even in those primitive times, they had properly built roads that have been trodden until now, making them flat, well-drained, and wide enough that even cheap carriages have a decent ride.

So Qing grumbled about being needlessly excited, and only after spending the entire winter and finishing her copying with plenty of time to spare did she finally leave the Divine Maiden Sect.

"""Have a good trip!"""

As usual, with the Divine Maiden Sect disciples' enthusiastic send-off behind her, Qing began her fifth year of her Jianghu Journey.

\textit{I can't believe I'm already in my fifth year.}

\textit{Time really flies.}

Qing was suddenly filled with a strange sentiment about this.

However, passed time is something that always flies by in an instant, even if it was the most boring and longest time in one's life.

"Have a safe trip, Physician!"

"But I have to go home after it's over…"

Tang Lan-Ah, who had settled in because she had to go to the Wulin Conference anyway, was an extra.

Still, she seemed to enjoy being enthusiastically sent off, smiling wistfully.

And then they stopped by Zigui, the city in front of the Divine Maiden Sect, to pick up Jian Buxi who had been left there.

Zigui, Xue Clan Trading Company.

Every time they came out to purchase supplies for the Divine Maiden Sect, it had grown a little, and now it had completely become a respectable estate.

\textit{As expected, the neighborhood's top intellect seemed to have a knack for business too.}

Qing accepted this, but in reality, this too was essentially a Zhongyuan business entity of the Heavenly Demon Divine Cult.

The capital came from the Cult, and the goods dealt with were connected to the Cult's trade ships, so Xue Ganom was little more than a figurehead who had lent his name.

This was the Heavenly Demon Divine Cult's terrifying economic invasion towards Zhongyuan… No, it was the result of Cui Liweng plundering the Heavenly Demon Divine Cult's secret connections to pile up gold and buy delicious things for Qing.

The real owner of the trading company was Cui Liweng.

Qing, who had already become familiar with the company employees - the guards at the main gate - waved at them and strode inside.

Then, in the middle of the main hall, the beautiful Xue Ganom, who had been giving instructions to the porters, raised his eyebrows when he saw Qing.

Jian Buxi had described him as looking like a 'Sister' with her limited vocabulary, and seeing him in person, it made sense.

With distinct features that were more handsome than beautiful, and a martial headband wrapped around his forehead, he looked like a cool cross-dressing beauty even to Qing's eyes.

"Wow, Xue Ganom. You get prettier every time I see you."

"Starting with insults as soon as we meet, I see."

"How about that person? Are they doing well?"

Qing looked around.

She clearly remembered seeing a lovey-dovey couple the last time she came.

Xue Ganom spoke calmly.

"We broke up. After thinking about it, she said she didn't want a husband prettier than herself. She couldn't live her whole life being called the ugly one compared to her husband."

"Oh my. Cheer up. I guess it wasn't meant to be."

"What do I have to be upset about? There are plenty of women who like me."

It's a bit annoying since he seriously thinks that.

However, when it came to women who like her, Qing wasn't far behind, so she just thought, 'Welp, I guess that's how it is'.

"Well, if Xue Ganom says so, I guess that's how it is. I'm going to Kaifeng. Where's my Sworn Sister?"

"If you're coming, you should have sent word in advance so that seductress could prepare. How can you suddenly show up and demand her? Should she just play around waiting for you every day? She went out to work."

"Wouldn't it be nice if she could just play around? When will she be back?"

"That might be fine for you. The old man already sent someone as soon as you entered the city, so she should be back soon."

At this, Qing narrowed her eyes.

"What's this? Did someone tail us? How did you know as soon as we entered the city?"

"Your companion is quite eye-catching, isn't she?"

While people might think Qing was a common ugly woman because of her face veil, the Tang Lan-ah beside her was actually, lo and behold, counted among the Five Great Beauties of Zhongyuan.

Even if she kept glancing at passing women's chests as if she wasn't, with an attitude like a boy in the prime of his youth.

Even though she saw her every day at the Divine Maiden Sect, she had rarely made eye contact.

She was busy looking hard, thinking the person's eyes were on their chest.

In any case, even so, her appearance alone was that of a supreme beauty with a fierce temperament.

"What's with that look? Your gaze feels unpleasant somehow."

"It's nothing. As long as you're happy."

"…?"

"Oooh, that person working over there, their chest-"

At the same time, Tang Lan-ah's head whipped around.

"Huh? Where? Where?"

"They've trained their chest muscles well."

Tang Lan-ah immediately glared with fierce eyes.

Qing let out a deep sigh.

\textit{She might not have been completely normal from the start, but she didn't seem like this kind of person before.}

\textit{How did she end up like this?}

She was already worried about this journey.

\textit{Jian Buxi was originally a bit lacking in the head, so it would be fine if I guide her well, but this one is a goddamn physician, yet somehow she's becoming more and more dumb.}

It was a time when the shoulders of Qing, the sole person with any common sense, felt heavy.