\chapter{Journey to Kaifeng (6)}

"It might sting a little?"

"Don't great physicians and Divine Doctors insert needles without the patient even noticing? Don't they stick needles in chickens and make them walk around?"

"The Nine Needles of Joy? Wow, you know about that too? But it's not good if you don't even notice the needles. What are you, an assassin?"

And then soon, Sting. Stiing. Stiiing on the shoulder.

"Is this right? It hurts for quite a while."

"Huh? Why isn't the needle going in?"

The strongest human body doesn't even allow needles.

Tang Lan-Ah pressed the needle firmly with a flustered look.

"No, what kind of muscle is this? A rock? Why, won't, this, go, in, ugh."

"Hey, it hurts. Ow. It hurts, you know."

"Just bear with it a little. Ugh."

Originally, when inserting needles, one should hold the needle body with the thumb and middle finger, gently press and rotate it to insert it to the correct depth, and sometimes gently tap stubborn areas with the index finger.

However, as it only dug into the elastic skin without penetrating, Tang Lan-Ah, who had been struggling, finally adjusted her grip on the long needle.

She gripped the needle body with her whole fist, the tip pointing down, and firmly blocked the end with her thumb.

Anyone watching might think she was holding a dagger or an ice pick rather than an acupuncture needle.

"Hey, aren't you going to remove your Protective Mirror? Why are you blocking even the Protective Qi with the needle?"

"Uh, wait, I'm not doing this on purpose, okay, now it's do- OW!"

With quite an intense pain, THUNK!

The sensation of the needle digging into the shoulder was vivid.

"Ah."

It was the doctor's startled voice.

For patients, it's a terrifying nightmare-like sound whether it's during medical treatment or surgery.

"…I think I just heard a sound that a physician should absolutely never make."

"No, no. It's not like that."

"Did I mishear? Oh, hiya, this is amazing. The pain seems to have decreased a lot?"

"Huh? Really? That shouldn't be possible…"

"Um… Doctor?"

"No, it's just. I stuck it in deep. Can you try moving your fingers?"

"Huh? Um, they're not moving? Is this normal?"

"They'll move by morning. Probably. But since it's completely numb now, the needles should go in well. Now then, sting."

Squish, squiiish,

Along with the sensation of intense pressing, Tang Lan-Ah spoke in a frustrated voice.

"Tch, it won't go in…"

Qing thought quietly to herself.

\textit{I should have received scientific Western medical treatment instead of these quack traditional physicians after all.}

\textit{It's truly a thousand-year regret that there are no Western doctors.}

However, there was another fact that Qing didn't know.

Western medicine of this era focused on more fundamental treatments rather than solving individual symptoms.

Where is the source of pain?

The brain! Let's remove the brain!

Where is the source of disease?

The rectum! Let's remove the rectum! 

The back! Let's remove the back!

This might sound like a lie.

But look.

Westerners suffered greatly from toothaches. So the personal physicians of noble aristocrats practiced preventive medicine by extracting all teeth even before they hurt, even for respected royalty.

What? Sterilization? Wash tools and hands?

That's something only crazy germaphobic lunatics do!

Wait, what? Mental illness? Yes, the brain! Let's remove the brain!

For reference, the development of Western medicine in this era was like this.

Doctors compared scenes they saw in dreams, and then chose the one from the person with the loudest voice to record as knowledge.

The concept itself was different from the start.

Traditional medicine was about treating sick people, so doctors who failed in treatment had to be prepared to be stoned.

But Western medicine was more like an attempt to try and save someone who was going to die anyway.

If successful, great, and if it failed, well, the person was going to die anyway, so the doctor wasn't at fault.

If by chance the patient survived, it immediately became the discovery of a new treatment method, adding another horrific tool to their arsenal.

So Qing should have been grateful to Tang Lan-Ah, but…

"Ah."

"What is it now?"

"No, don't worry. Maybe you'll be able to move your arm by lunchtime tomorrow… probably?"

Qing thought again.

\textit{Being a traditional physician was her only redeeming quality.}

\textit{But now it seems she has no redeeming qualities left, huh.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Breakfast for people in Zhongyuan is quite simple.

If that's how it had to be, Qing was willing to give up being a person of Zhongyuan.

"That, um, soak it well. Aang."

Qing ate the dumplings Jian Buxi offered like a baby bird.

If you wrap even simple stir-fried vegetables in torn dumplings and eat them, it's truly delicious with a spicy and sour taste.

What to do when your arm doesn't move.

Strictly speaking, it was more due to Tang Lan-Ah's crude acupuncture relying on force rather than the injury.

From Tang Lan-Ah's perspective, one might say, what else could she do when the needle wouldn't go in, but still.

Qing could have used chopsticks with her left hand.

But there was no need to go that far in a relaxed meal setting with no competitors.

Rather, the competition was on the feeding side.

As soon as Qing swallowed, this time Tang Lan-Ah held out a large chopstick-full.

"Wait, eggplant, take out the eggplant."

"What's this, you don't eat eggplant? You shouldn't be picky."

"I only like it fried, though? And I've already grown as much as I'm going to grow, so why eat a balanced diet to grow more? Hey. You. Again. Where are you looking?"

"No, it's just because you said ‘grow'…"

While this was going on, Zhuge Lixian was staring as if entranced.

Since his gaze was different from Tang Lan-Ah's, Qing's reaction was also different.

"What is it, Zhugie? Never seen someone eat a lot before? Am I fascinating? I haven't even eaten half yet, though?"

"If you ask if it's fascinating, it is indeed fascinating. But, Sister, your arm seems uncomfortable, may I ask what happened?"

"Huh? It's nothing. I got the wrong acupuncture in the middle of the night and it got paralyzed."

Answering ‘no' to a subjective question, Qing couldn't bring herself to say she had properly ruined one arm while teasing their little sister.

At any rate, she didn't lie.

"Ugh. Th-That's why I'm feeding her. No, what's with you, I'm just thinking of you…"

"I appreciate that. Hmm, should I get another treatment?"

"Now that I'm a bit more used to it…"

It was a rather unreliable statement.

But as Tang Lan-Ah said she was being considerate, and although it was just paralyzed, the effect was properly showing, so what could she do.

Since it would be good to arrive at the next city, Xiaogan, by evening, they left the Zhuge Clan early after breakfast.

Qing briefly considered staying one more day as Zhuge Xiang clung tightly to her leg.

"Sister, when will you come back? Will you come to get me?"

Qing burst into laughter.

As expected, little kids easily give their affection and easily forget.

It's all in vain to love them because they're cute.

When you see them later when they've grown up, boys become creepy and girls become stingy, so there's really no nutritional value in getting close to little kids.

Qing casually answered while patting her head.

"Alright. I'll come get you when you become pretty."

"Hehe, I'll be waiting, Sister."

Thinking, an adult who just took one walk with her at seven years old will be forgotten in a few days, and later she'll ask "Who are you?"

The journey in the Zhuge Clan's carriage was an extremely comfortable one.

While not quite as good as the Demonic Cult's ebony carriage, it was an invention of the Zhuge family, experts in mechanisms that provided a comparable ride quality.

Moreover, there was no chance of unnecessary trouble.

Far from trouble, people miraculously cleared the way in front of the carriage with the Zhuge character attached.

Traveling comfortably like this, they continued their journey straight north, finally entering Henan Province and reaching Xinyang.

Xinyang was a city with a large lake on its left leg, and this lake was Nanyang Lake.

However, Nanyang is the name of a neighboring town quite far to the west.

"Do you know why the lake in Xinyang is named Nanyang Lake? I should explain from the time of the ancient State of Xin during the Spring and Autumn period. At that time…"

Zhuge Lixian suddenly started automatically firing off an explanation about this.

It could be said to be a truly strange thing, as no one had particularly asked.

"…And so, it was later separated into Nanyang and Xinyang. Ah, speaking of Nanyang, it's the place where Ancestor Zhuge Liang spent his childhood, so I can't help but feel particularly emotional. Also, in the past, Liu Xuande\footnote{courtesy name of Liu Bei} served as the county magistrate there and visited Ancestor Zhuge Liang three times, so the story of the Three Visits to the Thatched Cottage happened right in Nanyang…"

As the topic naturally flowed to Nanyang, it seems he wanted to talk about Zhuge Liang.

Well, who could resist bragging about their family's greatest ancestor?

However, Nanyang is the neighboring town, and this is Xinyang.

Not long after the Zhuge Clan carriage entered the city, a group of martial artists rushed over, which was a touching competition of nearby orthodox martial officials rushing to welcome them.

Qing saw a familiar face among them.

"Ah. So this is the place."

No wonder it looked familiar.

"Aren't you Young Master Wang of the Daijing Sect?"

It was Wang Xunxi, the heir of the Daijing Sect.\footnote{Chapter 46}

Wang Xunxi also recognized Qing.

Qing had her face covered, and because of that, she had physical characteristics that made her even easier to recognize.

If she had her face uncovered, he might not have recognized her.

"Ah! It's Young Lady Ximen! Have you been well?"

"I've been…"

Qing, who was about to answer as usual, hesitated.

How cold and harsh that winter was, after picking up that Fushen-di and returning.

And then those Demonic Cult bastards were real sons of bitches.

\textit{Thinking about it again makes me angry, I should summon the Heavenly Demon later and destroy some things to vent.}

"Young Lady?"

"I've been getting by. I don't think I can say I've been well even as a polite lie…"

Wang Xunxi broke out in a cold sweat.

It was a difficult statement to respond to, so he had no choice but to change the subject.

"Th-That! Ah! You must be on your way to participate in the Wulin Conference? Oh, this young expert accompanying you must be the famous Beastly…"

Wang Xunxi's words stopped abruptly.

Unfortunately, it stopped at "Beastly," so it looked like it ended with "He's of a Beast!"

It was all because of Tang Lan-Ah.

While Qing was treated harshly, Tang Lan-Ah was a proud member of the Five Flowers of Wulin, the Speaking Poison Flower.

Only the members of the Zhuge Clan with their unique aesthetic standards would say 'How beautiful', and continue their exercises. This reaction of rendering men speechless was the normal one.

"What's this, Qing'er, is he someone you know?"

"I briefly stayed… Or wait, thinking about it, didn't the Daijing Sect people owe me? What do you think?"

"Y-Yes. Our Daijing Sect received a great favor from Young Lady Ximen. But this truly beautiful young lady…"

It could have been a somewhat rude statement, but in fact, Wang Xunxi didn't really understand what Qing was saying.

Right in front of him was a dazzling beauty, after all.

"I'm Tang Lan-Ah."

"The Speaking Poison Flower!"

Qing thought as she watched this scene.

\textit{This makes me want to have a title too.}

\textit{Just saying the name automatically triggers exclamations.}

In fact, Qing does have a title.

It just hasn't spread widely.

She had an impressive title called the Divine Sword of Crescent Moon.

Even bestowed by the Sect Leader of Mount Hua, Yuha Jinin!

It's not just the Crescent Moon Sword, but the ‘Divine' Sword of Crescent Moon.

To give the title of Divine Sword to a young girl who's about to insist she's officially twenty years old.

It was also a grandiose title that would make everyone sneer.

In fact, that's why it didn't spread.

People thought either the Mount Hua Sect Leader had gone senile, or he was shamelessly flattering the Female Mad Dog by gilding a young girl.

Since they didn't sincerely believe it, it didn't spread.

It was a problem caused by the title being too grandiose.