\chapter{Alone on the Path of a Lonely Person, Longing for the End of the Sword (3)}

It was the move shown by the old man.

\textit{Was that grandpa the Celestial Martial Emperor?}

What was embedded in her mind was not just a single Movement.

Free Practice Points could not be used on the Nine Swords of Solitude.

Instead, every time a Movement was filled through the respective Absolute Sword Walls of the other Nine Sects, the mastery would increase by one star.

After collecting all nine, thus reaching Nine Stars, there was information written that one could reach the realm of Ten Stars through a special mission.

It was information she had neither seen nor heard of before.

{\itshape Is it even possible to have something as unpleasant as this shit in my head?

Martial Arts Window, it's you again, isn't it?

You motherfucking piece of shit.}

However, considering she was attacked by this monster of a Status Window that felt like it ate her brains, it wasn't as filthy a feeling as she expected.

{\itshape Somewhere along the way… Something? Something? Swomthwing?

Seemed like a really great opportunity?

But it felt like someone interfered?

There was, I think? But I'm not sure? What it is?}

In truth, Qing had taken about two steps into the door of Demonic Ascent, before returning.

Demonic Ascent!

It was a kind of loophole that Demonic Adepts who had gone beyond the Transcendent Realm entered instead of the Unrestrained Realm.

It was a much easier method than overcoming the wall of the Unrestrained Realm.

However, the side effects were quite severe.

Typical symptoms included a murderous impulse, a sadistic disposition, and a predilection for cannibalism.

To be fair though, it wasn't all that different from Qing's current state.

At any rate, if one entered the realm through Demonic Ascent, they would go batshit crazy and become a Demonic Adept.

And until they reached the next realm, it would continue to be as such.

Only when a Demonic Adept overcame the wall and entered the Profound Realm did they finally regain their sanity and return to normal.

This was called Demonic Descent.

However, in the long history of Wulin, there were only a few who returned through Demonic Descent.

They were bastards who easily overcame the wall through a loophole.

And after, since they had to overcome even higher walls, they had to suffer several times more than martial artists who had properly ascended to the Unrestrained Realm.

At any rate, Qing had returned from almost falling into the eternal pit that was a Demonic Adept.

It was thanks to the great Senior, Celestial Martial Emperor, who magnificently led her out of such a state.

Unfortunately, Qing had no memory of it.

People often erased memories when they received a strong shock for the sake of recovery.

It was a type of ultimate move called, ‘Why don't we pretend it never happened?'.

The experience of being antagonized by the entire universe had long surpassed the level that Qing's fragile and pitiable mind could withstand. In fact, she might have not even been able to kill a bug.

At any rate, if there was no memory, she didn't know.

And Qing didn't think deeply about things she didn't know.

It was natural for one to not remember something if they tried to forcibly hold onto it.

She already knew that if she just let it be, it would naturally come to mind.

It was a similar concept to the oh so high-quality jokes that ahjusshis would suddenly remember while they were lying down, thus ending up chuckling.

Qing sent an awkward smile to her companions who were looking at her with worried eyes.

"I'm alright. I'm sorry for worrying you."

Peng Daesan frowned.

"Are you certain you are truly fine? It is a bit difficult to say you are alright when you have bled this much."

"I did?"

Instead of answering, Peng Daesan just pointed at a spot.

Following the direction of the end of his finger, there was a dark pool of blood.

It was far too extraordinary of an amount to have come from a human.

Normally, if you vomit that much blood, wouldn't you just die?

Qing denied it.

"What's that? It's not my blood!"

"...Did you not just vomit it out?"

"Ehhhh, me? I don't know anything about that."

"You even asked to thump you on the back."

"Did I?"

Qing sneakily hid her blood-stained sleeve behind her back.

"Can you not be serious for once? Just in case, circulate your Inner Qi to check your Qi and blood."

Qing obediently followed Peng Daesan's words.

Her Inner Qi, practically overflowing from her dantian, gently circulated through her entire body's acupuncture points, swirling around her Fine Meridians1.

\textit{How to put it? It seems more natural than before?}

Despite the speed of the Inner Qi flow being faster than before, the control of the flow had still become easier.

Basically, it had become possible to deliver much more Inner Qi in one strike than before.

"Oooh? What's this? It's gotten much better, huh?"

"Better?"

"Is this what happens if you vomit blood? If I throw up again, won't I just reach the Transcendent Realm? Is this what Enlightenment is?"

Qing made a huge fuss.

Peng Daesan experienced firsthand that when a person was too flabbergasted and incredulous, words simply could not escape the lips.

That was when Qing turned her gaze to Liuhe Zhenren.

"Elder Sect Leader. That's a trace left by Senior Celestial Martial Emperor. Apparently, it's called Thousand Changes."

Liuhe Zhenren's eyebrows twitched.

"Thousand Changes? What is it that you mean?"

"It's that Movement. The martial art is called the Nine Swords of Solitude, so-"

"A sword sought lonelily by oneself! How can this be! Oh my world! Sword Friend! What is the meaning of such a beautiful phrase! How can such stirring words come from that rough and unruly mouth?! Then, that is the Celestial Martial…Emperor………. Mm."

Nan'gong Shencai interrupted.

Spit flew out of his mouth and a frenzied glow glittered in his eyes due to his overzealous excitement. However, upon receiving a ferocious, sharp glare from Liuhe Zhenren, he suddenly mimicked the persona of a solemn young man.

{\itshape But, by the way? Somehow? Wasn't there? An unnecessary addition in the middle? Why? How?

I'm pretty sure he dissed me, right?}

As Qing cocked her head, pondering Nan'gong Shencai's dialogue, Liuhe Zhenren urged her on.

"Youngest Sister. Please, tell me in detail."

"I saw like some kind of illusion. Some grandpa transformed into a sword? And then he used Sword Compression like this or something."

"Sword Body Unification! Sword Compression! Indeed, the Celestial Martial…Emperor… Mm."

"CAN YOU! NOT! JUST! STAY! QUIET!"

"I apologize. It slipped out in spite of myself…"

Nan'gong Shencai turned courteous once again.

However, his politeness was slightly different from Qing's.

It was not out of fear of Liuhe Zhenren's might.

It was out of respect for one of the most renowned swordsmen of Jianghu.

After all, Liuhe Zhenren was a ‘true swordsman' worthy of Nan'gong Shencai's respect.

While Nan'gong Shencai shrank back, Qing described the technique she saw in the illusion to Liuhe Zhenren.

She had promised to, after all.

She had agreed to share if anything came to mind.

It was a technique she had acquired without any effort, either way.

Furthermore, it was an Insight gifted by the Celestial Martial Emperor to the Mount Hua Sect.

\textit{It's not even mine, so I should just share it and enjoy the findings together.}

"I see! You have read his Sword Marks! A divine talent! You are truly a divine talent! Can you perhaps demonstrate it once?"

"Of course!"

Qing drew her sword triumphantly.

And then, just as her brain and body remembered-

Just as she remembered…

Qing merely glared at the innocent Moonlight Sword (No. 8).

"Uh. Um…"

"What is wrong? Youngest Sister."

"I don't know how to combine with a sword. And I can't use Sword Force either…"

The Movement she had painstakingly learned was utterly useless.

It was impossible for a martial artist in the Late Stage Peak Realm to replicate the supreme Force2 Arts that the Celestial Martial Emperor had mastered only in his later years.

Qing's shoulders drooped.

"Ah…"

Liuhe Zhenren lamented.

Though she had read the Sword Marks, since she was only at the Late Stage Peak Realm, it was natural she could not replicate it.

"The inexplicable principles of Sword Body Unification are still beyond the Youngest Sister's experiences, I see."

However, Liuhe Zhenren didn't seem disappointed at all.

"As the Youngest Sister's realm rises, you will naturally come to realize it. The Insight left by Senior Celestial Martial Emperor will surely help in breaking through the wall."

"Really?"

"Of course."

Liuhe Zhenren's internal evaluation of Qing soared vertically.

From a Rising Star with a strong backing, to a Hidden Dragon, a Divine Sword, who was worthy enough to aim for the next generation's Greatest Under Heaven.

And of course, building relationships with influential figures was an ingrained instinct unique to the Chinese people.

"You must be tired after vomiting such blood. Rest well and let us prepare a big meal tonight to replenish your energy. How does that sound?"

\textit{Food!}

Qing's eyes sparkled.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had a very lively week.

It was thanks to the sincere hospitality of the Mount Hua Sect Leader.

In fact, the extent of their closeness had people whispering whether the Mount Hua Sect Leader had found a long-lost daughter in his old age, thus bringing her home.

Apart from the sect disciples, numerous guests were staying at the Mount Hua Sect.

Naturally, these guests also took turns attending the dinners, that were at a level of grand feasts, held over the week.

As a result, it practically became a situation where Godmother Ximen Surin's named disciple was officially participating in a Wulin event.

Liuhe Zhenren went out of his way to offer genuine hospitality, and if asked to choose the climax of such a reception, it was this.

‘She is like the incarnation of the Yue Maiden herself, a peerless talent that will be called the Divine Sword in the near future!'

There were various ways titles were created in Wulin.

And among them, some were created with the endorsement of someone who held incredible authority.

Furthermore, Liuhe Zhenren had laid it on a bit too thick.

So much so that guests who visited the Mount Hua Sect had a title mistakenly engraved in their brains for the great Godmother's named disciple.

The Divine Sword of Crescent Moon!

Among the characteristics for a person of Jianghu, there was a habit of being unable to resist sharing a fact known only to oneself.

Later, guests who left the Mount Hua Sect did not hesitate to talk about the fussing scene that the Sect Leader made, as well as the female expert, a new divine star, who had appeared in the Orthodox Faction.

Of course, they were unaware that this Orthodox female expert actually took pleasure in killing people and wielded the Demonic Arts.

Nonetheless, Qing was enjoying herself.

Yet, all pleasures had to end eventually.

"So, what are you planning to do now, my Youngest Sister?"

At some point in time, Qing had been promoted from the Youngest Sister to ‘my' Youngest Sister.

"I'm thinking of going back to the Divine Maiden Sect. It's been quite some time since I've seen my master. I told her I would return around this time."

"I see. Very well, then. Feel free to visit us again anytime. It would be very nice of you to share stories of the world with an old Senior Brother like me."

The Mount Hua Sect Leader himself had come out to send her off.

If other Sect Leaders from the Nine Sects had seen this, they would have clicked their tongues and frowned.

'How could he be so ignorant of his own status and dignity, thus acting like some snobbish vulgarian?'

However, Liuhe Zhenren had always been known for his extremely secular nature anyway.

The current prosperity of the Mount Hua Sect stemmed from such characteristics, so Liuhe Zhenren was proud regardless of what others said.

"Take care of yourself too, Changbin. See you again someday."

"Please take care as well, Young Lady Ximen…"

Changbin replied while stealing glances at the Sect Leader.

As the Great Senior Brother of his generation name, Changbin had to re-enter training at the Mount Hua Sect for a while.

And besides him…

"It is time to return to my clan."

"Indeed. It should be around time Father's wrath cools down. Moreover, I cannot be away for too long, after all."

"What the! San! Sword Friend! Are you saying you're going to leave me?"

Peng Daesan let out a deep sigh.

He had once prided himself on being far and away the greatest among the Rising Stars, thus regarding his title of Jade Qilin as shameful.

However, that pride had been shattered.

Now, in Peng Daesan's heart burned a passionate desire to train and reach the next realm.

Above all, he did not want to lose to this woman.

Qing's occasional taunt, ‘You're weaker than me, you know?', inexplicably ignited an uncontrollable fury within him.

Because, for some reason, he felt his insides boil again, Peng Daesan took deep breaths to calm his emotions.

"If you ever visit Hebei, make sure to stop by our clan. I will make sure you are fed with so much delicious food that your stomach bursts."

Peng Daesan took out a wooden box from his possession, fiddled with it, and then handed a piece to Qing.

"Ooooh. What is supposed to be the meaning behind this?"

"When in the world will your way of speaking…Nevermind. Forget it."

Qing received the wooden plaque offered by Peng Daesan.

It was a block of wood with the name ‘Peng Daesan' engraved on it.

"It is a plaque of proof that you are a guest of the Peng Clan. Even in the case that I am not there, the clan will welcome you as a guest and treat you well."

"That is right, I see! Sword Friend. Take mine as well. If you ever visit Anhui, stop by this Sword Brother's house. After all, a swordsman should undoubtedly visit the Greatest Sword Clan Under the Heavens at least once."

Qing received two guest plaques.

\textit{Well, I guess it's kinda like a business card.}

It was a roughly accurate concept.

However, there were different levels for even guest plaques.

Qing was unaware that the plaques she received were of the highest grade, Special Plaques reserved only for distinguished guests.

With that, the group parted ways, each heading to their own homes.

It was nothing to be sad or lamented about.

If fate allowed, they would meet again.

And even if it didn't, they told her she could go visit their homes.

No matter how fun something was, it would eventually have to end and one would head home.

After all, what was more important than such enjoyment was the fact that she now had a home to return to.