\chapter{Alone on the Path of a Lonely Person, Longing for the End of the Sword (1)}

The Mount Hua Sect!

People did not hesitate whatsoever to regard Mount Hua as a great sword school.

Of course, whenever this was mentioned, someone who pushed for the Wudang Sect always appeared.

From then on would be an argument, going at each other's throats without abandon.

It was the beginning of a fierce sword debate.

‘The Violet Mist Sword of Mount Hua is truly a peerless Divine Art.'

Are you looking down on the Purple Mist Sword Qi right now?

‘However, do you perhaps not know the polar principle of Wudang's Tai Chi?'

Yeah, okay. And? Wisdom Sword of Cosmic Harmony! Eat this instead!

As emotions intensified like so, some, who had no connection to the major sects of Wulin, would claim to represent them and initiate proxy battles.

And that moment was when the spectators would cheer the most.

This was the mere level of entertainment in the primitive ancient times of China.

At any rate, if one were to choose the most outstanding sword sect among the numerous factions in Wulin, the Mount Hua Sect and the Wudang Sect would naturally come to mind.

That was the position Mount Hua held in Wulin.

However, for Qing, it didn't matter whether the Mount Hua Sect was ranked high or low.

The important part was that she had been tricked, she had been backstabbed, and she had been quite possibly bamboozled.

"The mountains are pretty and all, but where is it?"

The rugged mountain terrain, one of the five great mountains of Zhongyuan, instilled a rather polite and respectful heart in anyone who gazed upon it.

There were no slopes in Mount Hua.

Only sheer cliffs.

The white things are cliffs, the red things are trees.

This was an apt description that summarized the terrain of Mount Hua in autumn.

It was a month's journey to the Mount Hua Sect.

In Qing's opinion, there had been significant changes during this time.

Changbin had finally stopped babbling and started actually speaking!

Of course, he still could not clearly distinguish between formal and informal speech, thus using it awkwardly.

He also didn't seem to know that he should at least pretend to look at someone's face when speaking to them, a form of common sense that even Qing was aware of.

Still, since he had overcome the divine punishment of being mute through his own efforts, she could understand at least this much.

That meant Changbin still had room to grow even further.

\textit{Since I'm the oldest in this party, I should embrace him with a warm gaze and ample attention………}

"The Mount Hua Sect is located on Purple Night Peak, so just a little m…"

"No, I'm not talking about the Mount Hua Sect. Where are the volcanoes\footnote{Huasan}? I don't see any smoke, you know? Is it a dormant volcano? Like, is it playing around? Or unemployed? Did it leave to go fetch some milk?"

Changbin smiled brightly.

It was somewhat a smile befitting a Daoist.

\textit{Seems like he's trying act like a Daoist since we almost arrived at his home, huh?}

"Young Lady Ximen, I see you, too, make such a cliche joke. It is something everyone who comes to Mount Hua for the first time says at least once, so this Daoist here has already heard it dozens of ti……."

Changbin trailed off upon seeing Qing's grave face.

"It truly was a joke, ri…?"

Qing maintained her grave demeanor.

To be frank, it was a rather brilliant response of itself.

Qing yelled in exasperation.

"This is seriously so upsetting! My volcano! MY LAVA!"

"Young Lady Ximen, if you raise your voice like that…"

"Since when did Mount Hua become yours?"

Peng Daesan rebuked her.

"It could be, you know? This is pure bait! I got baited so hard! My volcano! I wanted to see lava! Flowing fiery rivers! Intense heat! By the way, what's delicious here? What dish is this place famous for?"

"…?"

The shift in topic that was as smooth as water was like the mysterious principles of polarity and unity in Tai Chi Yin and Yang.

Peng Daesan was momentarily taken aback by how miraculous it was.

"Haha, Sword Friend, Mount Hua is not a restaurant. And in the first place, meals in a Daoist Sect can not be considered gourmet. Expecting too much shall only lead to disappointment."

"Eh? Wot? The meals at the Divine Maiden Sect were hella delicious, though. Everything you just said? It's just prejudice, you hear me? Prejudice."

In fact, the meals at the Divine Maiden Sect were truly tasty.

Even though it was made with just ordinary mountain herbs, there was a certain specialness that came from its subtly deep flavor and aroma.

This was actually the case for a majority of female-led sects.

Unlike men who would be moved to tears at the mere sight of meat, tearing into it like beasts, for women, meals were a significant matter.

At any rate, the group members did not particularly mind Qing's attitude.

After all, though she grumbled in complaint, Qing was actually enjoying the scenery of Mount Hua.

Her gaze constantly swept over the surroundings.

Whenever they reached a spot where the terrain was majestic and beautiful, she would stop and look around, just like a country girl going sightseeing.

In truth, Mount Hua was an incredibly rugged mountain.

It was not a place suitable for leisurely strolls and sightseeing.

However, there was not one person among the group who was not a Master. So, this wasn't exactly an issue for any of them.

And finally, upon reaching the Lotus Flower Summit2, the gates of Mount Hua Sect came into view.

Mount Hua was relatively close to the secular world for a Daoist sect.

In fact, it was quite excessively close.

When joining a Daoist/Buddhist sect, one's name would be put on record.

This was called Register Entry, a ceremony where one left behind their secular name and received a new Dao/Dharma Name.

However, there were also disciples who were recorded, but did not abandon their secular names.

These were the secular disciples.

Each sect had its own criteria when it came to the initiation of secular disciples.

For example, the Divine Maiden Sect did not accept secular disciples.

Instead, if a woman decided to leave because she had found a man or claimed she could not live without a man anymore, the sect would only break her dantian and return her name, thus displaying tolerance.

And in fact, it was a remarkably merciful leniency.

Other sects would sever the tendons of the limbs and then generously stamp the expelled with a burning seal as a parting gift.

Moreover, Daoist/Buddhist sects would rigorously examine a person's character and qualities before accepting them as secular disciples.

There was a rumor that the amount of donation could significantly benefit one's character score.

There was no official response to this, however.

In this regard, Mount Hua was known for its lenient stance, to the extent of being criticized by other sects that were even Daoist like them.

Their qualities are decent and they aren't a bad person? Accepted.

Their qualities are actually really decent? Accepted.

By the way, their family is really wealthy? Accepted.

Mount Hua had their own reasons, too.

Since a neighboring sect has taken over the entire land of Shaanxi, we might as well earn something from the secular disciples, right?

The land was all but taken away by the neighboring Zhongnan Sect; moreover, they were considered a legitimate Daoist sect with ancestral rituals held throughout the entire year.

At any rate, for these reasons, Mount Hua disciples were spread all over Zhongyuan, and thanks to this, the Mount Hua Sect was relatively wealthy, with my people overflowing its main mountain.

The result of that was a sprawling complex that completely filled the Lotus Flower Summit.

Qing looked at such a scenery in surprise.

{\itshape Woah. How can a single sect be so massive?

The Divine Maiden Sect is like a tiny shop in comparison. What the hell?}

Changbin looked at Qing with a pleased smile.

The disciples guarding the sect's main gate and signboard warmly welcomed Changbin.

"Great Senior Brother, have you returned?"

"Young Expert Peng and Young Expert Nan'gong, it has been a while since we last met, hasn't it? Oh, but who might this Young Lady be…….? Could it be?"

"As expected of Great Senior Brother! We have always believed in you!"

"A fiend among Daoists who can captivate any woman with just a breath! How did the world create women yet also birthed Changbin! This is the esteem that Changbin of Mount Hua holds! Remember his name!"

The fault lay in Changbin's usually frivolous words and deeds.

To the Junior Brothers, Changbin was a great man who would have beauties from all over Zhongyuan courteously following him and competing for his attention with just one word - ‘Alcohol'. After all, according to his dogma, it was not right for one to drink alone.

Changbin's face turned red.

"N-No, i-it is not like that. This is Young Lady Ximen, a distinguished guest here to greet the Sect Lea……"

"Greetings to the Sect Leader?! Do we get to suck on candies now?!"

"OOOOOOOH, CANDY! Hey, guys! Great Senior Brother will be throwing candy!"

"Wait, Junior Brothers, wait………"

And then, without even giving Changbin a chance to stop them, the disciples rushed inside, shouting ‘Candy, candy'.

The sophisticated Movement Technique of Dark Fragrance swiftly slid among the people of the Mount Hua Sect.

The expression ‘receiving candy' meant the same thing as ‘eating galbitang3' in modern Korean vocabulary.

To put it simply, in ancient primitive China, candies had to be distributed to guests at wedding celebrations. Thus, they were implying that Changbin would soon be wedded.

\textit{Why did it just so happen to be that one of the loose-mouthed bastards are manning the main gate today?}

The rumor was bound to spread throughout the sect by the end of the day.

Changbin awkwardly retracted his hand and glanced over at the party cautiously.

"About that. Ahem. Little Brother Peng? It was not my intention, so please do not look at me with such menacing eyes. After all, I am still your senior……."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was when they had sent word of their arrival to the Sect Leader's temple and was sitting in the temple's annex, having drunk half a cup of tea.

A call came to come up immediately.

It was truly a rare occurrence.

Normally, once one reached the status of a Sect Leader, they would possess a certain gravity, so they wouldn't just scurry out because a guest wished to see them.

Moreover, when it came to ‘face' culture of the ancient, primitive, barbaric China, guests were to wait in line according to their status.

After all, arbitrarily changing the order could be a great insult to other guests.

Yet even so, the Sect Leader urgently summoned the next Great Disciple.

The reason was simple.

Changbin was twenty-nine this year.

And it had now reached a time when autumn was in full bloom.

As such, just a few months later, he would become an old bachelor who was too late to find his match.

A man had to have a family, by any means necessary.

It was a happy event for a man to become the head of a family and enjoy the affection of kin. Furthermore, it helped a man maintain a balanced life while walking on the path to the Transcendent Realm

So, it was an incredibly crucial time for Changbin. How could he not meet the woman that his bachelor disciple had brought?

Thus, Liuhe Zhenren \footnote{柳河 真人. Yuha Jinin in the original text}, the Righteous Iron Plum Blossom and Sect Leader of the Mount Hua Sect, hurriedly welcomed the guest.

"I see. So you are that child."

"Do you know me?"

"I only just heard about it as well, you see. Yes, that brilliance in your eyes is undoubtedly the mystical aura of…Daoism…Mm. It is overflowing with mystical aura, but… Mmmm. It is not just a mystical aura that is overflowing, but also…"

Liuhe Zhenren thought to himself.

{\itshape What is with this child?

The eyes that bore the unique brilliance of Daoism were profound, so the realm she had reached in such qualities was far from ordinary.

But what was this sinister madness that was stuck in-between?

Such a dreadful thing was definitely not normal.

After all, there was a kind of uneasiness that could not be expressed with mere written descriptions.}

"Uh…"

As Liuhe Zhenren struggled to find the words he wished to say, Changbin quickly added an explanation.

"Great Master, this is Young Lady Ximen, the named disciple of the Godmother, Elder Ximen Surin."

"Ah! Senior Ximen's!"

Thunder struck in Liuhe Zhenren's mind.

{\itshape Senior Ximen's named disciple!

Then, it made sense for her eyes to hold a bit of madness.

Ahem. Of course, of course.}

Liuhe Zhenren was immediately convinced.

Ximen Surin's female-oriented ideology had become significantly milder with age, thus reaching its current state.

As such, only the previous generation of Masters knew just how vicious the Zenith Among Women was in her heyday, when the female activist shouted, fought, and advocated for women's ascendancy.

And at the same time, he realized one other fact.

{\itshape She must be the youngest sister who suddenly appeared in the record of generation names!

Moreover, unlike that other Ximen, her face was full of bright smiles, making her look extremely amiable.}

Liuhe Zhenren, who suddenly had a younger sister despite being over fifty years apart in age, smiled warmly at her.

"Hoho. I never expected to see a youngest at this old age. Is Senior Ximen doing well?"

"Yes. She was in good health the last time I saw her."

"Is that so? But it appears that our youngest's attainments are not low whatsoever. Can you perhaps tell me?"

"I'm still only at the Late Stage Peak Realm."

"Oh! Oh! A great blessing has come to the White Path Orthodox Factions!"

Liuhe Zhenren did not skimp on his admiration.

{\itshape To think a young girl of only twenty was at the Late Stage Peak Realm.

It appears that Senior Ximen has been raising a monster.

After all, even Senior Celestial Martial Emperor had not reached the Middle Stage Peak Realm at such an age.}

Liuhe Zhenren's warm gaze became even warmer.