\chapter{Alone on the Path of a Lonely Person, Longing for the End of the Sword (2)}

"I see, did you come to see the Absolute Sword Wall?"

"Yes. My Sword Friend over the- No, I mean, Young Master Nan'gong said that one just had to see Mount Hua's Absolute Sword Wall."

"Hoho, the Absolute Sword Wall is the Insight gained by our great senior, the Celestial Martial Emperor, after witnessing the Sword of Mount Hua. It is also a divine relic of our sect. We cannot show it carelessly to outsiders."

It seemed it was not a spectacle shown to just anyone.

Originally, Qing thought that no matter how beautiful nature's scenery could be, it wouldn't be all that impressive. However, the breathtaking view she saw while ascending Mount Hua was beyond imagination.

After all, as a worker who had lived only within industrial complexes in the past, this was the first scenic masterpiece of the world she had seen.

Although Korea's landscape was beautiful, its scale was modest and didn't overwhelm people.

As such, Qing couldn't hide her disappointment.

"Ah, is that so…"

Then, Liuhe Zhenren smiled warmly.

"However, since the youngest is a part of our Daoism family, it would not be right to call you an outsider."

"Then can I see it? Am I allowed to?"

"Instead, if you think of something after seeing the Absolute Sword Wall, would you tell me? With the talent that our youngest holds, you might see something different."

"Of course. I'll write down a review that fills an entire page, without missing a single thing."

"Hoho. You do not have to go that far."

Of course, Liuhe Zhenren truly didn't expect that.

Even the greatest Masters of Mount Hua could only feel the overwhelming gap in skill upon gazing at the Absolute Sword Wall.

What could a mere young girl at the Late Stage Peak Realm possibly understand?

Peng Daesan and Nan'gong Shencai, sitting behind the conversation like a folding screen, exchanged glances.

It was because they found this situation incredulous.

For those from the noble clans, the Mount Hua Sect had passed on the responsibility of a mission as the price for viewing the Absolute Sword Wall.

It was neither difficult nor dangerous but was extremely troublesome and success was not guaranteed.

Hence, they had been wandering around Jianghu in order to complete the mission instead of staying comfortably in their clan.

Of course, it was not mandatory for the mission to be done with all their might.

However, since they had seen the Absolute Sword Wall, they had to at least pretend to undertake the mission given.

They couldn't just return to their own clan and immediately sprawl leisurely.

And yet…

Here the Sect Leader was, babying and fussing over Qing, ready to show her the Absolute Sword Wall right away.

They were aware of the warmth and affection between the Daoist sects.

However, they could not help but feel that such differential treatment was excessively unfair.

But Liuhe Zhenren had an entirely different perspective on this.

Even if they were from the Five or Ten Noble Clans… Even if they were rulers of regions said to be a part of the Orthodox Faction, in the end, they were people who, at a moment's choice, would prioritize family over the greater good.

Senior Celestial Martial Emperor had also said the same thing.

That only the Mount Tais, the great pillars, of the Orthodox Faction truly cared for all under the Heavens.

And even among those pillars, those grand mountains, Godmother Ximen Surin stood particularly tall, reaching an astounding peak.

As such, the reason why he was so lenient on Qing was not because of the Divine Maiden Sect, but rather due to Ximen Surin herself.

Furthermore, the present times were already filled with signs of ominous divination.

It wasn't without any reason that the successors of the clans were allowed to see the Absolute Sword Wall and their debts were cleared.

If the signs of divination came to pass and great trouble arose for Mount Hua, perhaps the goodwill of Qing could be leveraged to borrow the power of Ximen Surin.

Of course, the fact that he found the youngest so adorable and lovable, as she seemed almost like a granddaughter, also played a part.

As one aged and gained status, seeing the young ones hesitating in their presence became all too common.

It was natural to fall for the ever so bright and assertive youngest.

"Hoho. I would love to talk more with Youngest Sister, but as the leader of a sect, I am far too busy. There are so many who wish to meet me that I cannot afford to spend much time like this."

"Ah. Are you busy? I shouldn't bother someone who is so hard pres……."

"We do not have much time, so let us quickly go and return. I can spare at least this much time for our new Youngest Sister."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Celestial Martial Emperor's realm was not known to anyone.

However, what was well-known was that he had reached the level where it was possible for him to ascend to an Immortal before the age of sixty.

Also, that he has chosen to remain on this earth instead of ascending.

He declared that he would not become an Immortal until he had seen the extremity of martial studies, a stern vow famously known as the Non-Ascension of Unseen Martial Peak.

Thus, the Celestial Martial Emperor traveled among the Nine Sects, obtaining the essence of martial studies and the secret martial arts of the sects.

According to unofficial history that had been passed down orally, it was rumored that the Celestial Martial Emperor had simply barged in and demanded their esoteric techniques, causing an immense commotion.

The truth was taken to the grave by the Seniors of the previous generation, thus making it an unknown mystery.

However, even if he was the benefactor who saved the entire Wulin from the conspiracy of the government, it was still hard to understand how they could so readily hand over the secrets of their sects. That couldn't be denied.

So, instead, the Celestial Martial Emperor left the Insight he had gained from observing the esoteric martial arts in the form of Sword Marks.

That was exactly what the Absolute Sword Wall of the Nine Sects signified.

Some criticized why something left by a great senior of Wulin was monopolized by the Nine Sects.

But regardless of such complaints, the Nine Sects stood firm and proud.

The place where the Celestial Martial Emperor left these Sword Marks was enough of an explanation in itself.

It was a location difficult to find and blocked on all sides, thus preventing outsiders from casually observing. Why else would he have engraved the Sword Marks here?

It was a gesture of consideration, so that not just anyone could see his legacy.

He had blatantly made it a gift intended for them, the Nine Sects, rendering any outsider's criticism moot.

This was the story shared by Liuhe Zhenren, awfully reminiscent of ones told by grandfathers.

As Qing listened, engaging and asking questions along the way, they soon found themselves at the entrance to a narrow canyon on a peak.

After traversing the cramped canyon, they reached a basin surrounded by cliffs.

And there stood the Absolute Sword Wall.

"Oooh……."

Qing let out an exclamation.

Simply put, it was a giant cliff filled with densely packed, petal-shaped scars.

Truthfully, it wasn't all that shocking or mind-blowing.

And she wasn't even sure if those were made by a sword or were the result of some natural erosion.

After all, the grandeur of the landscape, blending with the uplift of the earth, was honestly a more astonishing sight to her.

Qing thought.

But still, since he showed her with such sincerity…

It was both polite and her duty to lavish praise for the kindly grandpa of the Mount Hua Sect.

And this judgment was exactly why Qing was so beloved and babied by the elderly.

Just as Qing was about to speak…

\begin{quote}
[Strange Fate Occurrence - The Legacy of the Celestial Martial Emperor]

[You have witnessed the Insight left by the Celestial Martial Emperor.]
\end{quote}

Suddenly, the world turned ash-gray.

One old man, the sole individual with color.

His hair, turned completely white, was tightly tied back.

He looked like a grandfatherly figure filled with stubborn determination.

While letting his hand, which held a long sword, droop, he stood quietly, closing his eyes and calmly breathing.

From the sword flowed white petals.

The blade scattering into snow-white petals seemed as if the sword was melting away.

And then, the sword moved.

Following the trajectory of the sword, countless petals blossomed.

The petals floated in the air.

Swept by the wind, they fluttered gently, landing softly only to suddenly fly up again with a guffaw.

Like a whirlwind, they swirled around, spreading across the vast blue sky without any lingering attachments and simultaneously filling the entire world with a rain of petals…….

Everywhere her field of vision reached, her eyes were dazzled by white flowers.

Alone in the maelstrom of painfully beautiful light…

Qing unconsciously reached out her hand.

But whenever she grasped at the petals that seemed to overflow the entire world and opened her hand, she found that she had caught nothing.

That was when a single petal landed gently on the palm of her hand, which she had been dazedly looking at with a sense of loss and regret.

Something that was not caught when trying to grasp.

Something that only came near when staying still.

Qing lifted her head.

The old man was no longer in sight; only a sword remained.

The old man was there, however.

After all, the old man was the sword, and at the same time, the sword was the old man.

Finally, the sword flew.

Each and every one of the countless petals were formed from concentrated Sword Force, the manifestation of Sword Compression1. And they all chased after the sword like a storm.

Starlight twirled, swirled, and frolicked with innocent laughter, plaguing and tormenting the cliff with traces and marks.

Qing looked at the cliff.

It was a message left by the Celestial Martial Emperor.

Strokes without rules, formed by incomprehensible sequences of random moves, wrote chaos, as well as a message.

A voice trickled out of Qing's mouth as she stood there in a daze.

\textit{"The flap of a butterfly's wings in the Qinghai Province's flower gardens can cause a storm to rage in Beijing. As such, all changes in the world are the harmony born from the will of a mere small and insignificant creature."}

It was as if I was speaking, yet it was not I who was speaking.

Qing did not even understand what she herself was saying.

\textit{"If even a small and insignificant creature can do that, then the will of humans, being so innumerable in the world, makes any change utterly unpredictable."}

Qing looked up at the sky.

The sky was cloudy and the surroundings dark.

\textit{"A Thousand Changes Leads To Ten Thousand Distortions. A veritable kaleidoscope. Can a human dare to understand the will of the heavens? Do martial studies truly place its truth beyond the nine heavens, in a terminal bud unreachable by man?"}

The old man despaired.

Yet, he never gave in.

Because it was in the face of despair that people showed their purity.

Since they were organisms that had evolved through such means and manners.

The old man opened his mouth.

\textit{"The heavens-"}

Suddenly, Qing's senses expanded.

She crossed Mount Hua, going beyond the lands of Shaanxi.

\textit{The disciples of Mount Hua laughed, chattered, and trained and in distant cities and inns, fights and disputes followed just as usual and in the bars, Ooooh, I wasn't intending to peep but how embarrassing, the sun hasn't even set yet. But what an interesting posture, huh? Wait, let me just watch a bit longe-}

Her senses expanded further.

\textit{Crossing Zhongyuan, over the highest mountain ranges of the world, ah, the red-skinned barbaric white fuckers. White fuckers eating swine soup, white fuckers burning witches, white fuckers clad in iron charging in the name of God……..}

And finally, after crossing the great oceans to brush past people in tents wearing feathered hats…

Qing finally faced the blue planet, soaring among the sea of stars.

The majestic universe unfolded before Qing's eyes.

The most beautiful sight a human could behold.

It was then.

All the stars twinkled at once, welcoming Qing.

The stars whispered in an ever so guileless and tender voice.

\begin{quote}
	\textbf{-Die.}
\end{quote}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The mouth opened.

\textit{"I will not seek the understanding of the heavens or the earth. I will only devote myself to walk alone on the path of a lonely person, longing for the end of the sword."}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Uwegh! Qing suddenly vomited blood.

Dark gore poured out onto the ground.

"C-Child!" "Qing! Are you alright!" "Sword Friend! The blood!" "Young Lady! Are you all right!?"

Four different voices slammed into her ears at once.

Qing waved her hand.

It was to signal that she was okay for now.

But her stomach was still churning, burning, surging.

"M-My back……."

Qing gestured towards her back.

Though she did not know who among the four it was, someone began thumping her back gently.

Then, the unfinished vomiting continued.

Guweeeegh, Hoo, Hoo, Guweeeeegh.

Along with the embarrassing sounds, Qing kept retching blood.

It was as if she was throwing up all the blood in her body.

After that, she felt strangely refreshed.

Qing wiped her mouth with her sleeve.

"Phew! Finally, I feel much better. Ahhhhh woahhh, how refreshing."

Her body felt strangely light.

\textit{Wait, is it just my imagination? Or did it really get lighter?}

"Youngest Sister, are you alright?"

"Ah. Just a moment…"

Qing opened the Martial Arts Window that continued to send her notifications.

A new martial art that had been added was sparkling.

A Purple Border, at that.

Then, she suddenly recalled one Movement of a martial art she had not known before.

\textbf{Nine Swords of Solitude.}

\textbf{Eighth Movement, Thousand Changes.}