\chapter{Journey to Zhongnan (4)}

The will of the stars was the fundamental nature given to each
individual by the heavens.

In the language of Zhongyuan, it was also called innate destiny.

The higher a martial artist's realm, the more they could do.

And humans, as creatures, had a peculiar trait of wanting to do what
they could.

The reason for this was unknown.

Even in Qing's homeland, there were countless people who did all sorts
of bizarre things simply because they could.

As such, the higher the realm of a martial artist, the more they were
unable to restrain their desires, and the more their innate nature
would inevitably emerge.

In fact, this was the difference between the Orthodox and
Unorthodox Factions.

Daoist and Buddhist sects were fundamentally composed of
practitioners, so even as their realms rose and they gradually became
omnipotent, they maintained self-discipline and cultivated their minds.

The safety mechanism of the Noble Clans, led by the Ten Great Clans,
was their face.

In order not to disgrace the name of their families, in order to maintain
their dignity, tey restrained themselves from doing things they could do but would
be criticized for.

However, the Unorthodox Faction was different.

The dream of an Unorthodox martial artist was to live as they pleased,
lording over the world as they saw fit, without any regard for others.

The higher their realm, the more intoxicated they became with their
power, thus committing increasingly heinous acts. If they crossed the
line, or if they were caught, they would immediately become Demonic
Adepts.

At any rate, for these reasons, every moment was a hardship for Qing's
True Qis.

The True Qis were Qing's will, her unconscious, and they also reached
into the deepest part of her subconscious.

At the same time, they were originally a flow that existed in nature, so
they borrowed the energy of the world for a while.

The True Qis were mystical energies that knew the intimate inner
workings that Qing herself was not even aware of, the functions and
mechanisms, and also remembered the flow of nature.

In fact, whenever there was a big issue, the Great Purity True Qi
suppressed it, but in truth, the Inner Qi Cultivation Technique that
suffered the most was the Zhu Yang's Heart Cleansing Mirror.

The Blissful Maiden Arts had concluded that since the owner was
endangered by the Heavenly Slaughter, it was best to divert that
murderous intent into lust to prevent a rampage.

But what do you know?

For some reason, even though this bitch was a peerless beauty and the
world's greatest temptress, her lewdness was not Yin Qi, but Yang Qi,
making her similar to a man.

As such, the functions and abilities of the Blissful Maiden Arts, with its
very name being so girly, had difficulty exerting its power.

So, the Blissful Maiden Arts asked the Zhu Yang's Heart Cleansing
Mirror, a fellow Daoist Cultivation Technique, for help.

Since it had its roots in the Daoist Sect, unlike Buddhist Cultivation
Techniques, it did not consider personal enjoyment as an affliction, but
acknowledged it as a longevity technique.

Moreover, the True Qi of the Zhu Yang's Heart Cleansing Mirror
contained pure Yang energy, a study that cleansed the mind and had
excellent effects in protecting the spirit.

Thus, it was also excellent at twisting murderous intent into lust
overflowing with Yang Qi, working hard without rest all this time.

Thanks to that, even as the Heavenly Slaughter grew thicker, Qing did
not go on a rampage and massacre everyone indiscriminately.

There was a side effect of her murderous intent being diverted
elsewhere, but… Since that was the original purpose, it was a bit
ambiguous to call it a side effect.

At any rate, the True Qis, which reached the very bottom of the
unconscious, always found a solution.

And now, at this moment when the Heavenly Slaughter had burst forth
upon reaching the Transcendent Realm.

Now that her realm had risen and she began to emit starlight on her
own, her True Qis, as her owner shook before the fate of Heavenly
Slaughter, went berserk, throwing their eyes open wide, as they
exuded an ominous aura.

Now, it had become completely overwhelming for them.

Prevention was difficult and treatment was difficult.

Before all, the center of her mind, her very foundation, had no
intention of becoming a practitioner.

As such, she did not feel any aversion to the Heavenly Slaughter, nor
did she make any effort to avoid it.

Just as one would look for food when hungry, she sought out evil
people who had done deeds worthy of death.

Even the selective activation of the Heavenly Slaughter was thanks to
the tearful efforts of the Zhu Yang's Heart Cleansing Mirror.

Nevertheless, the True Qis found an answer.

The True Qis decided to let it all go.

Trying to stop it midway would only leave an unpleasantly lingering
feeling of dissatisfaction and regret.

Instead, they decided to focus their efforts on the moment afterward,
when she felt great satisfaction and was full.

Therefore, the Buddhist and Daoist True Qis waited for their
opportunity.

Beside them, the Heaven-Shattering Demonic Qi, not realizing what was
happening, foolishly beat them up, but at any rate, they waited for the
moment to surge up all at once and suppress it.

And now, at the very moment when the breath of a villain who had
never once felt ashamed of his lifelong evil deeds was extinguished.

At this moment, when the nerve cells fired like molten iron from a
furnace, emitting all kinds of intense signals throughout the body.

The Buddhist and Daoist True Qis were unleashed all at once.

Sometimes, to put out a fire, one must add more fire.

Adding satisfaction upon satisfaction would leave a long afterglow,
making one not even look at it for a while.

And after a few repetitions, the owner would get into the habit of
raising the Buddhist and Daoist True Qis at the same moment,
sweeping away the Heavenly Slaughter.

Thus, following the lewd guidance of the expert in this field, the
Blissful True Qi, the Buddhist and Daoist True Qis threw away all face,
dignity, solemnity, and seriousness, tickling their owner's entire body
and running wild.

And since the Awakening True Qi, which had a significant connection
to the owner's subconscious, read the atmosphere and determined
there was no danger in the wide area, the Daoist and Buddhist True
Qis thrashed their owner, thoroughly mixing in their resentment for
always avoiding that damn Heavenly Slaughter and constantly
practicing Demonic Arts.

Until their owner's mind could not endure any longer, with her eyes
rolling back and foaming at the mouth as she fainted.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"……shì dà shén zhòu, shì dà míng zhòu, shì wú shàng zhòu, shì wú děng
děng zhòu, néng chú yī qiè kǔ, zhēn shí bù xū1……"

Seol Yee-ri woke up naturally, thinking that the voice reciting the
Buddhist scripture was truly clear and pleasant to hear.

And like a person who had just woken up, she enjoyed the lingering
sensation with her eyes closed, savoring the beautiful voice that filled
the space.

Until she suddenly got up in a hurry.

"Gate, gate, paragate, parasamgate, bodhi svaha. Ah. Young Lady
Seol. Are you awake?"

However, what greeted Seol Yee-ri was the warm smile of Qing, who
was sitting naked in the lotus position, reciting the Prajñāpāramitā
Sūtra.

Her eyes, which looked as if they had cleared away a great worry, were
clear and deep, shining transparently as she looked at Seol Yee-ri.
Seol Yee-ri tilted her head.

She wondered if Young Lady Ximen's eyes had always been so
immaculately clear.

It was to an extent where one might think of a famous, virtuous, and
highly respected Buddhist monk who had completely transcended
worldly desires.

However, she just accepted that Qing was naked.

She must have been naked while sleeping and she's naked now, so she
must just be someone who is always naked. Or something like that.

Rather than understanding, it was more like she just didn't care
because it had nothing to do with her. No questions asked. Ah. Coachman.

"Why are you like that?"

"No, it is nothing."

Seol Yee-ri abbreviated her words, thinking that she had a vivid dream
where a coachman suddenly attacked her and she fell unconscious
after taking some medicine.

Despite the revolutionary abbreviation, Qing just smiled.

Then, a hint of embarrassment suddenly crept into Qing's smile.

Her fine eyebrows slightly furrowed as she looked at Seol Yee-ri with a
troubled smile.

"Young Lady Seol. I know it might be obvious, but still."

"……?"

"Do you, by any chance, know how to drive a carriage?"

In truth, Qing had just asked without any expectations.

But, lo and behold!

"I do."

"Really? You can drive a carriage? You know how to?"

"Yes."

Seol Yee-ri nodded again.

Qing's eyes widened.

Her unusually clear eyes were filled with amazement.

Seol Yee-ri felt a bit proud, but then wondered if it was right to feel
proud about this.

Qing was truly surprised.

So very, very surprised!

What is this? A noble young lady, who was raised preciously and
doesn't even know basic common sense, much less any skills, can
actually drive a carriage?

How? Did she learn it for fun?

Wow. A beetle can also roll, huh?

To think she would have such a menial skill.

"Um. It seems the coachman has crossed the River of Three Crossings
and is on his way to meet the King of the Underworld. Apparently, he
had done this kind of thing more than once or twice. How could I let
such a vicious villain live? I didn't kill him because I just forgot. It was
something I had to do as a member of the Orthodox Faction, so it's
not my fault, but."

The reason why Qing considered it a menial skill was because driving a
carriage was actually a menial task performed by the lower class.

So, it was a bit embarrassing to ask someone to do it, even if they knew
how.

That was why her words became longer.

"So, could you perhaps drive the carriage, Young Lady Seol? It's better
than walking in this rain, after all."

"I shall."

Seol Yee-ri readily agreed.

Walking in the rain versus driving a carriage in the rain, of course, the
latter was overwhelmingly better.

At least, even if it was raining, one could sit comfortably while driving a
carriage.

Moreover, carriages usually had canopies for the coachman's seat, so
they would get less wet than those who braved the rain.

Besides, wasn't it Qing who had defeated the villain when Seol Yee-ri
had collapsed from the effects of the drug?

If it wasn't for that, who knew what kind of terrible things might have
happened.

Although it was funny that she had chosen that villain as a coachman
despite her bold words, it was obvious that one could be fooled by
someone who looked like a living Buddha, so there was no point in
blaming her.

As Seol Yee-ri got up to drive the carriage.

"Ah, right. Young Lady Seol."

Seol Yee-ri answered by looking at Qing silently.

Then, Qing said with an apologetic expression.

"Since you'll get wet driving the carriage anyway, could you leave your
dry clothes with me? And wear that instead. I'm sorry for taking back
what I gave you, but it's better than both of us being uncomfortably wet,
isn't it?"

Seol Yee-ri's forehead creased.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Thank you to Young Lady Seol, who is driving the carriage despite the
bad weather and a cold, no.

Is that even worth being thankful for?

She should have volunteered herself when we were looking for a
coachman in the first place, right?

Qing grumbled inwardly.

It was definitely not because Seol Yee-ri had left without handing over
her dry clothes.

Besides, she's driving so well.

Qing was already an expert on carriage journeys.

One might ask what kind of skill was needed to drive a carriage, but the
comfort of the passengers varied greatly depending on the coachman's
abilities.

Fundamentally, the roads of Zhongyuan were a mess.

Moreover, due to the uncivilized science of Zhongyuan, the
carriages lacked any form of humanitarian technological advancements
that considered the passenger's comfort. As such, the terrible road
conditions were directly transferred to the passenger's buttocks,
miraculously allowing one to experience the texture of every grain of
sand crushed by the wheels.

Therefore, the coachman had to carefully control the horses, maintain
speed, and minimize vibrations to reduce the burden on the passengers.

When it rained, the difficulty increased exponentially.

They had to determine whether the muddy water was shallow, a
bottomless pit, or a hole that would make the wheels wobble.

However, it was fundamentally dark on rainy days and the raindrops
streaking down further obstructed one's vision.

In that regard, Seol Yee-ri's coachman skills were already comparable to
the most skilled coachmen of even the largest stables.

Though it was a bit much to call her the best, wasn't it an incredible
skill to be able to compete with those who had driven carriages for at
least a decade, if not for their entire lives?

Of course, being a Master, no, being at least a High-Class Expert helped
immensely in seeing through the rain, but even considering that, um…

Was Young Lady Seol's talent really in driving carriages?

It's a pity that she was born in the wrong era and can't shine. I feel
sorry for her.

And so on.