\chapter{Journey to Zhongnan (2)}

It was out of the blue, a sudden remark of lewdness.

But Seol Ri didn't startle or frown. She just blinked and tilted her
head.

"Not a Master?"

The man who looked like a First-Rate martial artist at best had
brandished his sword so triumphantly that it seemed odd to her.

Seol Ri-Ri was a Peak Realm martial artist.

From Qing's perspective, she was just a fledgling who had barely
managed to reach the Peak Realm, but by the standards of the Central
Plains, she was still a young expert.

If one was to remove the 'young' part, there would be some debate, but
she was at a level where one could be called an expert.

"You stupid wench. For a novice, there is a novice's battle. Look at that
bitch over there, knocked out cold. Aren't you feeling sleepy?"

As he spoke, Seol Ri-Ri, who had been occasionally nodding off while
watching Qing sleep soundly, felt drowsy.

Her companion was asleep, it was raining outside, and the
coachman's skills were so adept that anyone would naturally feel
sleepy. That was what she thought.

"The… drug…"

It seemed that the slumping of her hand, as if no strength remained
within, wasn't simply because she was sleepy.

Only then did Seol Ri-Ri's expression turn serious.

"Keke, kehehe! I, I have waited for this moment, heh, you wouldn't know
how long! Everyone called me a fool! But I! Waited! For a time like this!"

"……"

"Keke, aren't you curious? What kind of mystical poison did I use to
make you so helpless, to make it so that you couldn't even hide the
gradual onset of the poisoning!"

"……"

"Kehe, it took five, five whole years! I spent five years' worth of income
just to buy this one poison. Everyone called me a fool! But someday!
Like this! I knew there would be a use for it! Wait, are you even
listening?"

Whether he was being listened to or not, Seol Ri-Ri was busy driving
her Inner Qi, trying to dispel the drug's effects.

The slowly accumulating poison was so subtle that it was only
noticeable after she heard about it and tried to circulate her Inner Qi.

"If someone is talking to you, you should listen! You wench who will
soon be moaning and groaning, just you wait until your husband
speaks!"

As the coachman shouted, he threw something down hard. The
something that was thrown onto the carriage floor kicked up a cloud of
dust.

"Keke, in just a little while, you won't even have the strength to lift a
finger. Then, whether you're a Master or not, you'll just be a wench
with a hole. I wonder how tight your hole is, kekeke, kehehehe."

And then, bang, the carriage door closed.

Seol Ri-Ri staggered up and kicked the carriage door, but strangely, it
wouldn't budge.

Then, Seol Ri-Ri gathered her Inner Qi.

A faint, whitish water Qi gathered in her hand.

At the same time, a cold air swirled and blew wildly in all directions.

Any martial artist with discerning eyes would have jumped up and
shouted with wide eyes.

Ice and Snow Divine Palm!

And so, bang! Seol Ri-Ri's palm struck the carriage door, and a loud
noise echoed.

Crack, white frost spread slowly in a circular pattern, centered around
Seol Ri-Ri's hand.

The inner wall of the carriage shattered with a crunch.

Between the cracks, a rather densely packed row of bars was revealed.

"Goodness. They even put iron bars in a carriage. They really went all
out, didn't they?"

"!"

Seol Ri-Ri's head whipped around.

"People are so rude these days. If someone is sleeping, shouldn't
everyone be quiet and tiptoe around? But no, they just make a racket
and bang on the walls. You really should consider those who are trying
to sleep."

"X-Ximen Sojeo? Are y-you ok?"

"Why don't you stop wasting your energy and rest? You shouldn't strain
yourself when you're not feeling well."

"But at a time li-…"

"Haa. This is why Peak Realm martial artists are all the same. They make
such a fuss over nothing."

A clear emotion rarely found in Seol Ri-Ri's expression appeared. It was
absurdity.

"Now then. Come here. If you act so rudely, they'll get scared and run
away. Bad guys are usually cowards, you know? They only come at you
when they think they can win, but run away the moment they think they
can't. And that's not good. I don't want to have a chase in the rain, even
if it's me."

As Qing spoke, she reached out.

Seol Ri-Ri tried to avoid it, but her body was sluggish and momentarily
lost strength, causing her to stumble. In an instant, a beautiful hand
grabbed her wrist and pulled her in.

However, it seemed that the carriage was already filled with a
sleeping drug, a paralytic, and even a Qi-dispersing drug that slowly
dissipated Inner Qi.

If only my body was in perfect condition, Seol Ri-Ri reproached herself,
but in reality, even if that were the case, nothing would have changed.

After all, Qing's No-Shadow Divine Hand was a Divine Art that
encompassed pickpocketing and grappling.

Seol Ri-Ri's body leaned helplessly and fell into Qing's embrace.

"What the. Were you circulating your Inner Qi again? Why do you
keep getting warmer? Hmm, but it feels nice and cool."

"What are you doing at a ti-…"

"Just stay still. So, I told you to be careful when choosing a carriage
and a coachman. They were all advice that would have been your flesh
and blood."

"You were the one who picked the-…"

"Ahem. It is not good to blame others."

"It's not someone else's fau-…"

"Ssssh. You can't do that. What will you do if a martial artist blames
others? Will you blame the one who stabbed you even when you get
stabbed? If you live wielding a sword, you should know that anything
that happens to you is natural."

What she said was true.

If you get stabbed with a sword, it's your fault for not avoiding it. It was
your fault for not defeating the enemy before that, for not realizing it
and avoiding it, for not running away if you thought you couldn't win,
and for not avoiding trouble in the first place.

Seol Ri-Ri shut her mouth, feeling resentful.

That was that, and this was this.

It's one thing for her to pick the carriage and the coachman all by
herself, but it's another to say that I was just sitting there watching
everything.

However, it wasn't entirely wrong to say that she just sat there and
watched everything unfold, so as a companion, she couldn't help but
feel that she was in the wrong.

Qing lay down on the carriage seat.

She placed the cool as ice jade ornament on top of her and held it in
place.

The jade ornament squirmed, trying to escape, but it was so weak that
it seemed the drug was starting to take effect.

"What are you thi-…"

"Hmm. I wonder if there are more in the group? And what should I have
for lunch today?"

"Don't be ridic-…"

"I don't want to, though? I'm going to be ridiculous. So what can Seol
Sojeo do about it?"

"I'll be ridic-…"

"Seol Sojeo can't do that. Only I can. Also, you're becoming more
unlikeable by the second. If you keep being like this, I'm just going to
abandon you right here and leave."

"I don't want that."

At that, Qing's eyes, which were giggling, turned wicked.

Because she was looking forward to what would happen next, to the
point where her murderous intent was at its peak.

How long has Qing been waiting for this?

When people in Zhongyuan evaluated a person, they looked at
their physiognomy.

Qing looked at it a bit differently.

Not in three dimensions, but rather, she could see numbers above their
heads, which were more accurate than physiognomy. Moreover, they
were not in the numerical system used by the people of the Central
Plains.

While looking for a coachman at the stable, she had found an
ultra supreme asshole. Wow! It's been a while since I've seen some
blood. It's a blood party! A blood feast!

And now, I can even use Sword Force, you know?

Normally, when people buy a new sword, don't they want to use it as
soon as possible? They want to stab, slash, and slice, testing how well
the sword performs and how it feels in their hand. If you're a martial
artist, it's only natural to be excited about the unveiling of a new
sword.

But what about Sword Force, which was not even a sword?

Her patience was almost at its limit since it was before the unveiling
of her Sword Force.

Now then, how will they react? Since he seemed like a coward, he
probably plans to wait until we're completely drugged.

How many will there be? I hope there are many, since it's been a while.
Qing's heart pounded.

But for some reason, no matter how long she waited, there was no
news.

How long am I supposed to wait?

I'm bored and I'm getting sleepy.

Is this a new type of assassination tactic to make people die of
frustration?

Thanks to this, the jade ornament had completely fallen asleep,
occasionally letting out a soft snore due to a stuffy nose.

The unique colors in Qing's eyes were gradually deepening, now
almost glowing faintly.

I'm bored. I might as well fondle her chest.

I feed her, put her to sleep, and even bought her clothes. If it wasn't
for me, this dumb bitch would have been loitering in front of the Grim
Reaper's door due to hypothermia last night.

So, it's only natural that I have this much of a right.

Qing's white hand slipped into Seol Ri-Ri's clothes.

Hmm. But it's a bit small.

It should feel good to have a handful to squeeze, knead, and clench, but
this is a bit……

It looks good, but it doesn't feel all that great in reality.

Oh well. What can I do? I'll just have to make do with this.

Oh, it's getting all hard. What a slut.

You should be grateful to me. I'm even playing with something that's
not all that fun.

Of course, Seol Ri-Ri might feel wronged.

After all, it was an inevitable physiological phenomenon that reacted to
stimulation.

However, since she was asleep from the drugs, there was nothing to be
wronged about.

Then, Qing's hand started to itch.

Come to think of it, squeezing the chest is supposed to hurt a lot. How
will she react?

Will this taciturn jade ornament scream? Or will she cry out and beg
me to stop in a way that doesn't suit her? How will she cry out? Will
she beg me to stop because it hurts, or will she curse and reveal her
deep-seated hatred?

What will her expression be like? Will she think she's been betrayed?

Or will she look at me with hatred, as if she had never trusted me in
the first place?

Either way, it sounds fun.

Qing's lips stretched into a long grin. It was a wicked smile that
seemed to reach almost to the base of her ears.

And right then-

Thud. The door opened.

"Finally!"

Qing jumped up and shouted.

"Keheueup."

Before the coachman could even finish his idiotic laugh, he was
dragged into the carriage by his jaw.

Qing's hand firmly gripped the coachman's jaw and lifted him up,
pressing his foot against the coachman's instep.

Moreover, the heel of Qing's embroidered shoes was only on the big
toe. The noisy heel of her embroidered shoes slowly dug into the top of
the coachman's foot.

The feeling of intrusion transmitted from the tip of her toes.

Crunch, the bones of his foot were crushed and then, sssssp, it finally
touched the hard carriage floor. Wow, it's pierced! It's cleanly pierced
through!

"Eeueup!"

The coachman, with his jaw firmly in her grasp, could only groan
through his nose, the hot breath warming Qing's cold hand.

"Hello? Friend? If you keep people waiting for too long, they might lose
their temper, you know? Now then. How many are there? How much fun
can we have?"

"Eueup."

"You're not going to answer? Then, it's going to hurt a bit?"

Qing's toes slowly lifted.

Then, she stomped on it again, about half an inch to the side.

Crack!

"Keueup! Eueueup!"

The coachman's eyes rolled back with just one stomp.

He's already fainting after just this?

She hadn't even started using her Sword Force yet.

Qing removed her foot and wiped the sole by rubbing it against the
floor, then switched feet and this time, aimed for, that's right, just
one.

Stomp!

"Kkeueup! Eueueup!"

The coachman's eyes immediately opened wide with just one stomp.

It was a single strike that made him wide awake.

"Now then. I'm going to let go of your hand now. If I find the sound
annoying, I'm just going to kill you, okay? Nod if you understand."

"Eup. Eup."

"Ah. I was the one blocking your mouth, huh. Then, do it with your
eyes. Nod if you understand and shake your head if you don't."

At that, the coachman's eyes began to move up and down vigorously.

He didn't even ask her to move his eyebrows, but it seemed like he was
overdoing it out of sheer enthusiasm.

Qing smiled contentedly at that and let go of his hand.

The coachman collapsed to the floor.

He didn't even dare to touch his pierced feet, just writhing with his
arms in an awkward position.

Qing squatted in front of him and made eye contact.

"Mister Coachman. What kind of poison did you use to make even a
Peak Realm Master so helpless? And where did you get such a precious
poison?"

"Heukjeom, I bought it from Heukjeom. And……"

It turns out that he had spent three gold pieces to buy those
extraordinary drugs.

It was also the decision of a man who had poured his entire income for
five years, with the determination to one day eat a precious woman that
everyone ridiculed him for, saying he was nothing but a fool.

And if it was such a precious woman, even if he ate her and then sold
her, he would still make a considerable profit.

"Ah. The Black Spot bastards again……"

It turns out that wherever one could acquire anything, poison was
naturally included.

I should have utterly destroyed all the Black Spot martial artists back
then. It's a shame I just ran away because they told me not to touch
them.

But regretting the past will only make one continue to feel regretful.

Rather, one should focus on the future and the things they currently
possess.

Qing had always done so.

As such, Qing did so this time as well.

"You didn't do this alone, did you? Your gang, no. Never mind that. How
many are there?"