\chapter{Journey to Zhongnan (6)}

Xueli's expression was faint.

It wasn't particularly due to the martial arts she had learned, as she was actually quite expressive.

Especially when she was splashed with water and calmly rebuked, her expression was quite a sight. One might say it was a vivid display of anger, sorrow, and the feeling of 'this is all your fault'.

Or perhaps she was just born with such a natural disposition.

So, sitting still and staring blankly at Qing, even though she wasn't speaking, if one were to just observe her, they would see her staring intently at Qing without a word. What in the world?

Of course, just because her expression was faint did not mean her emotions were shallow. She had very strong likes and dislikes, and even now, look.

Sitting at the table, staring at Qing, Xueli showed no particular expression, but if one were to look a little lower, they would see her fingers constantly moving without a sound, as if tapping a rhythm.

Originally, there were many emotions expressed when a person fidgeted with their hands, usually described as anxiety.

However, Qing did not need great insight to interpret that gesture.

"Young Lady Xue, are you drooling?"

"No, I'm not."

Xueli quickly wiped the corner of her mouth and rubbed her hand on the table, pretending nothing had happened.

But her voice was unusually lively.

Having fed her delicious food at every meal, she was now excited with anticipation at the table.

Isn't drooling in front of food something only dogs do? She's really like a dog. A bitch, in fact.

Pretending to be all haughty and whatnot, but drooling in front of food like a lewd bitch.

However, Qing had always been generous when it came to food, to the point of being considered a saint.

She would even feed enemies she was about to kill, so although Xueli was a bit of a nuisance, she was a travel companion. Well, maybe not exactly a companion, but more like a pet or a hot pack. Anyway, they weren't strangers, so wasn't it natural to feed her well?

Moreover, it was more enjoyable to eat together.

And giving someone delicious food and seeing them eat it well was rewarding in itself.

In that sense, Xueli was quite a good dining companion.

For one, she ate well and a lot.

It was an established fact, even in anthropology, that people from cold regions tended to be big eaters, and Qing thought that seeing someone eat heartily was much more pleasant to the eye than the dainty eaters of Zhongyuan.

But…

"Haaah, ah, haaah……"

If only she didn't make such lewd sounds and eat so vulgarly without any shame.

Xueli had a particular fondness for piping hot food.

When the thick soup was boiling, the inside was even hotter. Qing thought it was comparable to the temperature that would melt a spoon into liquid metal.

And yet, she would scoop up a large spoonful from the very depths of such thick soup without even blowing on it and stuff it into her mouth.

Then she would cool it inside her mouth!

The sounds of haaaah, ah, haaaah were all the sounds of her cooling the lava she had stuffed into her mouth.

What kind of table manners were these?

Is this really acceptable for the Glacial Palace?

It was a truly astonishing sight, whether she had some kind of heat resistance treatment inside her mouth, but the sounds were truly embarrassing.

Moreover, after swallowing the first bite, she would start to sweat profusely, and by the time she finished her meal, her silver hair would be soaked, with beads of sweat dripping from her chin.

"Young Lady Xue, you really sweat a lot, don't you?"

"Yes."

"But you don't usually sweat like that."

"I use Glacial Force."

"Even when you sleep?"

"Yes. So don't hug me."

"Why?"

"It's hot."

"Hmm."

Qing pretended to think deeply for a moment before answering.

"I don't want to."

At that, a vein popped on Xueli's forehead.

Regardless, Qing just snorted.

"You always say you don't like it, but when it's your turn to suffer, you get upset? Ehhh. Tsk tsk, you can't do that."

"……"

Xueli pressed her lips together tightly.

Because she had nothing to say.

"It's raining, so there's nothing to do outside. There's no particular fatigue to speak of, so there's no need to rest for a day. It's better to just depart immediately."

Qing liked the rain.

To be precise, she only liked watching it while hearing the pitter-patter through an open window from a warm or cool room, not getting wet herself.

She hated getting wet, damp, sticky, and clammy because of it.

One might ask how that was liking rain.

However, think of it this way; if it were snow instead of rain, everyone would like it when there was no need to go outside and it didn't involve the chore of shoveling it. As such, it all clicked into place.

A stable was one of the businesses in Zhongyuan, originally handled by the government but transferred to the private sector as peace continued.

However, it was a completely different concept from the privatization known in Qing's hometown.

To put it simply, it wasn't privatization but a forced handover.

You have horses and carriages.

But if the Emperor wants to use them, you have to hand them all over.

Until then, we will allow you lowly commoners to 'store' the horses and carriages for a while.

What? You don't want to?

Treason! Off with their heads!

So, stable owners were people who had to forcibly continue a business that would be completely ruined if the government requisitioned it at any time.

That didn't mean they were pitiful, though.

Stable owners made a tidy sum on the side by connecting travelers with bandits to rob them.

Since the horses and carriages would be requisitioned anyway, they thought they might as well earn as much as they could by any means.

Thus, another group of victims was created.

Two women appeared at the stable, and their beauty was truly out of this world.

They carried swords, so one should be cautious.

However, the taller woman's attitude was one of looking around cautiously, her shoulders hunched, and she seemed to be waiting for someone to ask her something, hesitating to speak up.

And the smaller woman had a blank, uninterested expression, but she was holding a palm-sized, flattened candy on a stick in her hand, sucking on it, giving off a very naive and foolish impression.

The stable owner cheered inwardly.

They were naive and inexperienced young women of Wulin!

"Are you looking for a carriage?"

"Ah, yes. That. A carriage. We're going to Chang'an……"

The stable owner's smile deepened.

They were complete novices with no travel experience!

What fool would look for a carriage from Luoyang to Chang'an?

Originally, carriages were to be returned and switched at the next city.

It was difficult to return carriages between stables if the distance was too far.

"I see, Young Lady. If you rent a carriage, you must return it at the stable in the next city and switch. Mm. If it's Chang'an, you can switch in Luoning."

This fucker, look at him.

Qing thought to herself, pretending not to know.

To get to Chang'an, one just had to follow the main road alongside the Yellow River.

The reason for sending them to Luoning was obvious.

It was a longer and more roundabout way.

"Yes, yes. But, how much money……"

"Ah. Well, carriages are a bit expensive."

"How, how much……"

"It depends on the carriage. How much did you have in mind?"

"About twenty silver taels……"

"Aigo. How can you expect to hire a coachman with just that?"

This fucker is trying to pull another trick, huh?

Connecting them with bandits and now overcharging them?

I can't stand to see that happen.

Contrary to her inner thoughts, Qing protested timidly.

"But, that should be enough……"

"Hmm. That won't get you a good carriage."

"Ugh. I guess it can't be helped. Let's stop by another stable."

Qing said this and held out her hand to Xueli.

At that, Xueli obediently took her hand.

Xueli was surprisingly compliant when it came to holding hands. When asked, she said Qing's hand was cool, so it was fine.

Whether it was one or the other, Xueli was not adapting well to the heat of Zhongyuan.

It wasn't that she wasn't adapting, but rather that she had no intention of adapting by continuously using Glacial Force.

Anyway, it seemed she liked Qing's cold hands, which were due to the White Hand Demonic Arts.

Whenever Qing offered her hand, Xueli would obediently hold it.

"Aigo. It's raining, why go through the trouble of going elsewhere? It's the same price here or there. Hmm. I can't help it. Since the Young Ladies are so pretty, I'll do you a big favor."

Thus, Qing was recommended the best carriage and a skilled coachman.

She didn't know about his driving skills, but judging by his Evil Karma, he seemed to have a busy side hustle.

Qing was like a anglerfish of the deep sea.

This anglerfish had a glowing lure on its forehead, and it was a hideous creature that would suddenly swallow any small fry that were captivated by it.

Qing had developed a taste for fishing for coachmen and was now waving her glowing lure, trying to catch one.

Twenty silver taels got her the best carriage and a coachman.

It would take three days to Luoning, or perhaps four or five due to the rain. It felt like she was being slightly ripped off.

However, she had plundered over two hundred taels from the bandits last time, so this much investment was nothing.

After boarding the carriage, Xueli finally spoke.

"The coachman is ugly."

"Hmph. You shouldn't say such bad things. He must already feel bad for being ugly, so how much worse would he feel if you say that to him?"

Xueli shook her head. As Qing had experienced before, it was a substitute for saying 'that's not it'.

What is it with her?

Why is she so obsessed with not being able to speak?

"He has a bad countenance."

"Eh. Are you going to judge a person by their appearance?"

Xueli shook her head again.

"(That's not it.) It was the day before yesterday."

"What? Did that guy from before do something to you?"

Xueli pressed her lips together tightly.

Xueli shut her mouth when she had nothing to say.

Then she focused on sucking on her candy again.

Qing admired her.

Wow. She really looks like a fool, doing that.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The lesson Qing learned from the previous incident with the coachman and its results was comparable to the enlightenment she gained during her second trip to Luoyang.

Joining a merchant convoy gives you free meals and pocket money!

Killing bandit coachmen is allowed and even brings in money!

Come to think of it, she gained that realization on her way to Luoyang, so what was it about Luoyang that gave her such great teachings?

Was it the White Horse Temple? The White Horse Temple, maybe?

I should have stopped by and offered some prayers.

Ah, that reminds me of the Buddhist chanting I forgot about. Qing picked up the bright verses of the Prajnaparamita Sutra again.

Go, go, to the hill of ascension. Completely.

Anyway, Xueli was useless as a travel companion, and since it was raining and gloomy, there was nothing to see outside, so Qing just diligently chanted for inner peace……… Zzzzz! Before long, she was snoring with her head lolling to the side.

However, surprisingly, nothing happened?

It turns out Qing was right; judging a person by their appearance was wrong. The coachman was kind, diligent, and drove the carriage well.

So they ate well at stops along the way to Luoyang and slept well at night. Although the timing was off due to the rain, he was very faithful to his duties as a coachman.

Huh. This isn't what I expected.

Qing was greatly disappointed.

However, there was one peculiarity.

"Young Lady Xue? Are you feeling sick?"

Xueli was sweating profusely.

Not just sweating, but to the extent that beads of sweat were dripping from her chin.

"No, I'm not."

"Why are you sweating so much? Your complexion doesn't look good either. You should tell me if you're sick."

Xueli shook her head. That wasn't it.

"It's hot."

"Huh? What about your Glacial Force?"

"Preparing for danger."

During the last incident with the coachman, Xueli had been helpless.

This was because she hadn't noticed the poison until it was too late, due to constantly using her Glacial Force.

And when she did notice, her Inner Qi was almost depleted, so she couldn't respond.

The same reason applied to why she caught a cold last time.

So, because of the suspicious-looking coachman, she had stopped using her Glacial Force in preparation for any possible danger.

And if she stopped using Glacial Force?

It was hot.

It was now early July. Even though it was raining, it was still hot. In fact, the humidity made it even stickier and more unpleasantly hot.

However, Qing had strong resistance to cold due to Cold Immunity and, as a side effect, a decent resistance to heat.

That didn't mean she wasn't hot, but it was just bearable if she stayed still, as the sweat and stickiness were less bothersome.

"It's not hot if you stay still."

Only after saying this did Qing realize the essence of the saying that elders always said, that it wasn't hot if one stayed still.

At that, a vein popped on Xueli's forehead again.

All Xueli had done inside the carriage was stay still.

Qing snickered and teased Xueli.

"If you're really hot, do you want to hold my hand? My hands are always very cold."
