\chapter{Journey to Zhongnan (11)}

Even with two Transcendent Realm experts, they were no match. Of course, both had been caught off guard by the most despicable of sneak attacks.

So it was no surprise that the underlings without Transcendent Realm experts would be no match either.

The only one who could wield a weapon with any skill was the Fan Master.

The rest had crude weapons, with two at the First-Class Realm and the others at the Second-Class Realm. But should they even be considered martial artists?

So, the Fan Master was somewhat capable.

Alright, I get it. This guy's level. He's around the Late-Stage Peak Realm.

He's so weak, I just want to kill him…

But since Seol Ri had asked to capture them alive, it seemed like she should yield on that part.

She wasn't exactly craving for bloodshed right now anyway.

"Isn't the promise different!?"

"What promise? Did we sign a truce or something? If we returned the hostage, we've fulfilled our promise."

"That's sophistry!"

It was indeed sophistry.

The hostage exchange implied an unspoken truce, which included allowing time to check the hostage's condition and provide urgent treatment.

However, one could deceive others with honesty, even more so because of its straightforwardness.

"No more words! Haha, how truly amusing! Those who have learned martial arts are just flapping their tongues."

In reality, if some Unrestrained Realm expert suddenly appeared and demanded a fight, Qing would also flap her tongue very diligently.

She would wag her tongue so hard that it would wear down and become sharp.

But Qing was a new Transcendent Realm expert, and the Fan Master was at the Late-Stage Peak Realm. Moreover, he had two First-Class Realm experts and several martial underlings with him.

If Qing had been in the opposite position, she would have taken up her sword, so this wasn't really an excessive measure.

"Now, here I go! My Moonlight Sword. Well. It's not exactly! Hungry!"

With a somewhat underwhelming battle cry, Qing stomped on the ground.

The heavy raindrops hitting her face felt quite intense. No, wait, the rain wasn't stopping, was it? It seemed to be pouring even harder.

She had enough leeway to think of other things, which meant Qing was underestimating her opponents.

And it was worth underestimating them.

With the first exchange, a hatchet handle was cut in half. With the second, a powerful palm strike of White Hand Demonic Arts penetrated more than an inch into the lower abdomen, causing the opponent to instantly collapse. The venomous energy of the Ten Great Demonic Arts immediately struck the dantian and tore through the meridians.

To his subordinates, it looked as if he had been hit hard in the stomach after his hatchet was cut, then collapsed, unable to breathe, going 'keo-heok-eok-eok'.

"Monster!"

Someone shouted and turned to run, the fear spreading instantly as they all showed their backs to Qing.

They even abandoned the young master they were supposed to protect at all costs, which was utterly ridiculous.

Qing scratched the back of her head and thought, 'Ah shit, I should have retrieved my binyeo first'.

Eventually, Qing had to chase after them.

The alarm bells were ringing continuously as she struck one with the hilt of her Qingzha Sword, another with the Moonlight Sword (No. 8), and another with the head of a hatchet that had fallen to the ground…… Eh, well, two of them were lucky.

When they all ran away at once like that, even a Transcendent Realm expert like her couldn't do much about it.

How could she manage when she was just one person and the enemies were scattering in all directions, especially when she hadn't learned any arts like cloning?

Thus, the Second-Class, or martial underlings, were quickly executed on the spot by cutting, stabbing, smashing, and tearing.

And then, there was the Fan Master, the two First-Class Realm experts, and the guy who was getting rained on while lying on the ground.

Wait, has the young master's bleeding stopped?

Oh dear, is he going to make it out alive?

Qing had smashed the limbs of the four and dragged them back, holding their hair two at a time.

At any rate, Qing's heart was full as she dragged the men by their hair, three in each hand.

Wouldn't Seol Sojeo be delighted?

This must be why fathers brought fried chicken on their way home.

But when they returned, Seol Ri's condition was far from good.

She was lying down, drooping, and only managed to lift her eyelids with difficulty at the noisy footsteps of the training gods. She then coughed violently, and blood trickled down the corner of her mouth.

Qing was startled and dropped the heads she was carrying, rushing to Seol Ri.

"Hey! Seol Sojeo? Are you okay?"

"Yes."

Hmm. She must be okay.

Seol Ri was the type to say she wasn't okay if she wasn't. She was someone with a strong opinion, even if she was incompetent.

Anyway, Qing immediately relaxed.

"Seriously, Seol Sojeo. How could you be in this state after failing to defeat just a few bandits?"

At this, a vein popped on Seol Ri's forehead.

"There was… a Late-Stage Peak Expert."

"It was just a Late-Stage Peak Expert, though."

"I'm… in the Early-Stage."

"Ah."

Qing was convinced.

She must be even more insignificant than I thought.

No wonder she didn't participate in the Hidden Dragon's Contest.

I mean, how could someone with only the Early-Stage Peak Realm dare to show their face in front of people?

But still, how could someone at the Early-Stage Peak Realm not defeat just one Late-Stage Peak Expert, two First-Class Realm experts, and a few Second- and Third-Class underlings?

If it were me, I would have ambushed the Fan Master first, smashed his head, and then dealt with the rest.

"Here. I've prepared the limbs so Seol Sojeo can handle them as she pleases. I even brought the Fan Master."

At this, Seol Ri seemed to try to raise her body, trembling in place.

Then, not succeeding, she flipped her body and tried to get up on all fours, losing her balance and falling a couple of times.

Qing watched this desperate attempt and thought.

Tsk. She's really making a fuss.

It didn't look like she was seriously injured, seeing how she kept trying to move even though she couldn't control her body.

Only then did Qing think, 'Ah. It's over', and her energy drained. As the excitement of the battle faded, she started to feel stinging and burning sensations all over.

Qing looked down at her thigh and muttered upon seeing the blood on her hand.

"Ah. I'm bleeding……"

The Body Protection Qi was not invincible.

Only the Embroidered Uniform Guard warriors, who strengthened their bodies with the cultivation method, could remain unscathed after being hit by all sorts of things with their Body Protection Qi.

However, Qing had transcended humanity, but she had not shed her human body.

Her muscles and bones were fine, but her skin was not protected, so the attacks she had blocked with her body while ambushing the Fan Master had cut her skin.

It wasn't a severe injury that bled profusely since it was only skin deep.

However, Qing hadn't used this method because she wanted to test how strong her body was.

Since there were many enemies, including a Transcendent Realm expert, she knew that she would be in danger if she didn't cut off the head before they could launch a proper joint attack.

If it was a one-on-one with just one Transcendent Realm expert, she might have been able to handle it, but facing a Transcendent Realm expert with numerous blades hindering her from all sides was not something even a Transcendent Realm expert could easily manage.

So, taking a few cuts to take the enemy's commander was a miraculous exchange.

If they had fought honestly, she would have had to be prepared to lose an arm or a leg, not just some skin.

As always, Qing's specialty was in cowardly fights, so if one were to closely examine her overwhelming displays, they were all either ambushes or against opponents who had lost their reason after being thoroughly provoked by her Infernal Mouth.

"Ugh, it stings."

There were two cuts on her thigh, one on her waist, and it felt like there were a few more on her back.

I wonder if this will leave scars……

Well, I can just apply the Tang Clan's medicine, but… I'm worried Master will get angry.

Yes.

If Ximen Surin found these glorious wounds, the strongest of the nuclear weapons, the neutron bomb, would surely fall.

But right now, Ximen Surin was just waiting for her disciple to return to the Divine Maiden Sect.

If at least Tang Nanah were with them, she would have nagged, 'I can't believe it. Why do you keep hurting yourself?', while meticulously treating her, but…

The only people here were a useless person with no use other than her face and a woman who was lying down, groaning, even more severely injured than Qing.

But her will was commendable.

"Keoheuk."

Seol Ri crawled on all fours to the Fan Master and struggled for a while, then lifted his frozen arm and smashed it, shattering it into pieces.

"Aaaak! Ugh, eubebe-"

Seol Ri shoved ice fragments into the screaming Fan Master's mouth. With his flesh frozen stiff, he desperately tried to push it out, making grotesque noises.

Wow! Shattered into pieces! Human shaved ice! Self-consumption!

It was an intense execution that she wouldn't likely see again in her life, and Qing's eyes sparkled.

Regardless, after struggling to change her posture, Seol Ri placed both hands on his crushed and broken leg.

Wow, she's vicious.

Even I wouldn't have done that.

Seol Sojeo also knows a thing or two.

If you're not vicious, you're not a martial artist. That's right.

It seemed the resentment from being beaten to a pulp was quite significant.

From the Fan Master's perspective, it might be unfair.

After all, he had told them not to injure the woman the young master would embrace with blades, so he had only used his feet, the back of the hatchet, and the hatchet handle.

If he hadn't, Seol I/Ri would have been rolling around in pieces by now.

This was why martial artists had to be ruthless.

If one showed mercy and spared the enemy, they would have to face the consequences.

The Fan Master couldn't even feel wronged because he was too busy dealing with the shock and the sharp pain from his frozen arm.

Thus, with only his frozen shoulder and thigh remaining, a man lay on the ground, retching.

"Ah. Seol Sojeo. He's not your enemy. Leave the young master for later."

Seol Ri turned to crawl towards the young master, but Qing stopped her.

Seol Ri obediently changed direction and crawled on all fours. The other bandits already had their limbs broken by Qing, so their limbs were twisted in unnatural directions.

Seol Ri approached them on all fours, and they could only scream and squirm.

Well. Let Seol Sojeo enjoy herself.

"Hmm. Young master."

"P-Please, spare me, please, spare me."

"That's not going to happen. If I spare you, you'll just bring your mom and dad to take revenge, won't you?"

"No, that will never happen-"

"Eh. Whatever. How do you want to die? I know how to use Freezing-Ice Arts too. Want to try being frozen? I just saw it, and it looks neat since there's no blood."

"Please spare me! Please spare me, I beg you!"

"Hmm."

Hmm. This isn't the feeling I was going for.

It should be more like, more intense, I can't help but want to see blood, a throbbing, uncontrollable anticipation.

Somehow… I'm just not feeling it…….

Suddenly feeling bothered, Qing lifted the young master and threw him towards a large puddle outside the roof.

Since she had quite a bit of strength, the young master's body drew a high parabola and landed with a splash, rolling on the ground with a broken bone protruding from his arm.

He screamed, but the sound was drowned out by the pouring rain.

She thought he would die on his own if left there.

And then.

Seol Ri finally managed to freeze and shatter the limbs of Qing's gifts, the Fan Master and the two First-Class Realm experts.

"Hmm. You're not finishing them off?"

"Yes. It's already over."

"Ah. Natural thawing. Hmm. Wouldn't it be faster to just leave them outside?"

Seol Ri nodded.

Qing lifted the Fan Master first.

Now then. Take aim. And throw!

The Fan Master's body, drawing a large parabola, landed right on the young master's body.

It was a heartfelt reunion of the two men, one that could not be watched without tears.

Qing threw the other two as well, landing them on the young master, and then Seol Ri lay down on her stomach, utterly exhausted.

"Seol Sojeo? Are you okay?"

"Yes."

"But you can't even control your body."

"Yes."

"Are you listening to me?"

"Yes."

Hmm. Is she normal……?

"If we stay here like this, we should find a room and rest. Hmm. It's about time to go down. Hmm?"

Then, Qing realized a big problem.

"Seol Sojeo. Just in case I'm asking. Can you drive a carriage?"

"I will."

It wasn't a yes or a no, but 'I will'.

She had the will, but this was a mountain path in heavy rain. She could easily fall off the road with the carriage.

"Hmm. Come to think of it, I think there were beds in the stronghold. These bandit types tend to take care of the leader's seat meticulously."

Come to think of it, there was no reason to rush down in this torrential rain.

Wouldn't it be better to wait until someone came, even if it was through the rain?

So Qing lifted Seol Ri.

"Keueup!"

A sharp scream was cut short by tightly gritted teeth.

"Seol Sojeo?"

"I'm, I'm okay."

"Hmm. Just bear with it a little. Let's see. Over there."

It was then.

KWAAAAANG! KUGUGUGUGU……!

It was an indescribably loud noise.

Not the kind of sharp, ringing sound from a nearby lightning strike.

It was the kind of sound heard from far away, but so loud that it could be heard through the ears and felt through the vibrations in the ground.

Qing's only thought at that moment was…

What the hell? Is it a landslide? Did a landslide just happen? 