\chapter{Journey to Zhongnan (3)}

"Th, There are twelve of them."

The coachman suddenly became very polite.

It was a very satisfying thing for Qing.

Indeed, if you don't know your manners, you should have your neck
chopped off, so that people will be polite.

Originally, manners and etiquette are characteristics that only appear in
those who are educated.

Because manners and etiquette are learned.

Only fools who haven't learned such things act rudely, thinking it makes
them look strong. But in reality, it's not that they look strong, but rather
that their parents look bad.

However, there was no compulsory education in Zhongyuan, so
there were many people who had never been taught manners.

Therefore, in Wulin, they used to correct people's manners quickly and
easily by placing a sword under their neck.

Like this.

"Twelve. Hmm. That's a little disappointing. Is that all?"

"Y-Yes!"

The coachman's eyes went dark!

To think she'd say it's disappointing even after hearing there were
twelve more. It was clear that she was not just any Master, but a
Supreme Master.

Damn it, he thought belatedly that he should have noticed when she
said she was not an ordinary beauty.

However, when he committed the act, the coachman had thought -

Ehh, whatever. In this life where I'm living like a bug, what's the point
of dying once when I could die twice. Before I die, I should at least lay a
peerless beauty down and crush her under me!

"But it seems like this kind of thing happens a lot? Everyone must have
been fooled by your innocent face, huh?"

In fact, there were two other coachmen with higher Evil Karma than
him. How could it not be, when coachmen were people who were
human traffickers, robbers, and rapists as a side job?

But those guys looked so menacing. If someone were to be assaulted
after hiring a coachman who looked like a criminal at first glance,
wouldn't it be closer to a natural death?

The reason why she specifically chose this guy was because he had a
very good impression. If it were modern times, he would have been able
to become a cult leader beyond just 'Do you believe in The Way?'. It was
because he had such a benevolent and gentle face.

He was born to be a son of a bitch, just right for producing innocent
victims, so I had no choice but to deal with this.

His Evil Karma showed that numerous victims had already held
funerals, but he had to prevent any more from being held.

"Now then. Shake it."

"Y-Yes?"

"If the carriage shakes a little, the other bastards will come running,
thinking someone is having fun. If the coachman calls, they'll be
suspicious, thinking why is he having fun alone and calling for us."

"Then."

"Why aren't you shaking it? Come on. Think of the carriage floor as a
pretty young lady. Hurry up and mount her, why don't you?"

Qing's blade turned black. Then, the blade of Moonlight Sword (No. 8),
which turned completely black, sprouted disgusting eyeballs.

Upon reaching the Transcendent Realm, she was able to melt and
handle the Heaven-Shattering Demonic Qi a little bit more.

Since it was True Qi that she couldn't use when someone was watching,
using it first when no one was looking was a way to use her Inner Qi in
a thrifty manner.

At that hideous sight, the coachman took a clumsy stance.

"No. Who humps a woman in such an awkward position? Are you doing
some kind of punishment? Push-ups? The carriage floor is a peerless
beauty, I said?"

At that, the coachman prostrated himself on the floor.

And then, he started to bounce up and down.

"Ah, come on!."

Qing's blade stabbed the floor, splitting the coachman's ear vertically.

However, when a blade was stuck right next to his head, no one would
scream because it hurt.

"Huek."

"Do it properly. Properly. You're humping a peerless beauty, but are you
just going to stick it in and shake it? You have to start with a kiss. Use
your tongue actively. Don't you know what that means?"

"Y-Yes!"

The coachman gained enlightenment once again.

He was not just caught by a Master, but by a completely crazy Master.

At that, the coachman performed with all his might, risking his life,
kissing and licking the dirty floor of the carriage, stroking it with his
hands, and making a fuss.

"Heehee."

Qing giggled as she watched.

"You seem to be putting too much effort into foreplay. Shouldn't you be
thrusting? Make the carriage overturn."

"Y-Yes!"

Thus, the carriage began to creak and shake.

Once it started moving with momentum, the amplitude gradually
became faster and larger.

Due to the coachman's desperate efforts, the carriage made creaking
and twisting sounds, cursing the fucking passengers.

Then, Qing heard the sound of footsteps rushing through the rain,
chatter, chatter.

-This bastard is having so much fun. Wow, the carriage is about to fall
over.

-Senior Brother, didn't you see what kind of woman was riding in there?
I already came once.

-You crazy bastard. How could you be so wasteful and ejaculate so
early? You have to go inside and make sure to close the lid properly so
that she'll cry and make a fuss.

Hmm. Senior Brother.

Qing quickly made her decision.

And finally, the carriage door burst open.

"Hey, if you're going to have fun, you should share. Mm?"

"Of course. Joy shared is doubled, sorrow shared is halved, and pain
shared is fun for me. I was just waiting for you. Now! Bang!"

Qing kicked the solar plexus of the man hanging on the carriage
entrance.

At that, the men entangled with each other and came tumbling down.
Qing lightly stepped on them and, oh, kicked, and oh, sliced their
tendons slightly with her sword, ah, this is so fun.

Since there were twenty-four ankles, but in reality, only half of them
needed to be dealt with, it was simple.

Thus, Qing stepped, oh, kicked, and oh, lightly sliced with her sword so
that the tendons would snap, wow, this is so fun.

Since a guy who was quick-witted turned his back to run, an iron hairpin
flew. The hairpin lodged into his ankle, leaving only the head of the
hairpin peeking out.

Because they were caught off guard, with some even having their
waistbands undone, and because their leader was already on the
ground, they fell in a heap, unable to respond properly.

Moreover, heavy rain was a friend that obscured vision, and the dark
clouds made the day dark.

In addition, there was a Transcendent Realm Master on a rampage, so
there was a mass occurrence of what were once ankles being crushed
under the steps of someone walking by.

But still, bad guys were bad guys.

As such, there was a lot of running, even with such disadvantages,
causing Qing's hairpins to fly, and fly, and fly, and fly. Thus, the very last
hairpin was in Qing's hand.

Her long hair, usually tied up and raised, was soaked in the rain and
hung heavily down to her knees.

It was an order from her teacher to keep her glossy black hair long and
not to cut it, even though it was a bit of a hassle.

Fortunately, the last hairpin did not have to ly into the sky, thanks to
the fact that everyone was rolling in the mud, clutching their ankles,
without a single one running away.

Qing gathered a bunch of her hair and tied it up on one side,
skillfully finishing it off with the remaining hairpin.

Then, she counted. One, two, three…… twelve, thirteen, fourteen,
fifteen!

What? There are three more?

Did you lie to me?

Of course, she could be subjected to this kind of joyful lie as many
times as they wanted.

But that didn't mean she could overlook the sin of trying to deceive
Transcendent Qing.

"Hey, Coachman. You said there were twelve? There are fifteen."

"H-How, already."

"Now. Explain. How are there three more? Can't count?"

"Th-That's not it. There were definitely twelve."

"What? Are you saying I lied? Now, come here and count."

"Ugh! W-Wait!"

Qing grabbed the coachman's ankle and dragged him out, sweeping the
floor.

Since the floor was muddy, the coachman struggled in the puddle with
a splat, splat sound, before barely lifting his upper body and wiping his
face.

In conclusion, the coachman did not lie to Qing!

It turned out that three friends had been brought along due to the
strong friendship among criminals, as they had heard that they could
crush a peerless beauty.

Hmm. That strong friendship. I should send them to the underworld so
that it can last forever.

Anyway, the coachman told the truth as far as he knew. However, one
can still deceive others even with an honest attitude.

"Then what? Are you saying the victim is supposed to be here? You deceived me in the end, so it's right to say that the coachman did the deceiving, yeah? Yes. Execution."

"W-Wait!"

"Don't yell yet. There's still plenty of time to yell later. Since your throat will get hoarse, it'll be hard for me to hear you, so you have to scream fresh for a long, long time. So, be sure to control the pace."

What is the difference between Sword Qi and Sword Force?

I'm also very curious about that. Now, let me do a little experiment to explore that.



Thus, Qing stabbed, sliced, diced, cut bones, trimmed flesh, peeled skin, and tried all sorts of things, alternating between Sword Qi and Sword Force.

This could be said to be the passionate practice of a great martial artist, seeking to find the fundamental difference between Sword Qi and Sword Force.

Sword Qi cuts well.

But Sword Force just cuts!

If Sword Qi feels like a 'swipe, swipe', then Sword Force feels like a 'SHING'.

For now, the victory in terms of hand-feel went to Sword Qi.

Sword Force was too sharp, so there was no particular sensation.

Zhong……, no, Qing was disappointed.

In fact, when one has high expectations for something, it is not easy for that expectation to be fully satisfied.

Therefore, Qing's heart was also like that when she used Sword Force.

This is why you shouldn't use a strong fishing rod even if it doesn't break.

If you attach a strong and stiff fishing rod to a large reel with good gear, you can easily pull up the fish without any effort.

But who goes fishing to just catch fish?

It would be better to just sweep them up with a trawl net.

In that sense, Sword Qi could be compared to a fishing rod, and Sword Force to a net pulled by a ship.

It was excellent and faithful to its original purpose of catching fish, but it was just tiring to enjoy, as if it were just labor.

However, when combined with the Invisible Divine Hand, it could create unexpected synergy.

Qing's Jade Maiden Sword was sharp enough to be handled like her own fingers.

And the Invisible Divine Hand was a secret pickpocketing technique that involved getting close enough to touch while maintaining a certain distance.

So, what if the distance was adjusted a bit closer, for example, between the muscles and the skin, allowing it to travel along the skin.

But what use was there in thinly slicing off long strips of human skin?

If she used this to write a book on necromancy, using the skin as paper and blood as ink, she might encounter something great in the future.

But Qing knew nothing about necromancy, so it was an unfortunately impossible future.

Thus, as Qing was fully enjoying her hobby, only the coachman was left in the end.

Qing approached the coachman with a faint smile, step by step.

Then, she suddenly had a thought.

Huh. What is it? I shouldn't kill this guy, that's what I thought. Why was that?

Why did I want to keep him alive? Was there a reason?

Qing carefully reflected on her thoughts.

The conclusion was, Hmm! I don't know!

I thought I had some kind of ingenious idea to kill him, but I guess I forgot.

As Qing approached with her killing intent, the coachman had already lost his mind.

It was understandable, seeing someone happily dismantling people while their mouths were wide open like demons.

In fact, even if his mind was intact, he wouldn't have been able to run away.

That was because both his feet were punctured and his shins were broken when he fell from the carriage.

Looking at the coachman's dazed face, Qing clicked her tongue and finally used the last resort, the White Hand Demonic Arts. Her hand, reaching under his solar plexus, grabbed his heart.

Wow! Now this is mine!

I can do whatever I want with this guy's heart!

I control this bastard's heart!

I am the ruler!

Qing squeezed his heart hard, as if a surgeon was performing the final, ultimate operation, forcefully circulating his blood.

When she tripled the heart rate, blood spurted out from all over his body.

As the blood pressure forcibly surged, all the blood vessels throughout his body burst at once.

His eyeballs, where all the blood vessels had burst, swelled up bright red. Oh, what's this? It turns red when the speed is tripled, huh? Is this how it works?

Eventually, as the last bit of life flickered out, that very moment, that very instant, that truly brief moment… 
