\chapter{Journey to Zhongnan (7)}

The coachman was surprisingly skilled, so aside from the fact that he
charged a bit much, took a longer route instead of a faster one, it was a
smooth journey.

And it was a very boring journey.

It was really boring.

It was raining, so they had to stay inside the carriage, and Miss Seol was
not very talkative, so she was no help in killing time.

She was pretty, and completely soaked, so there was something to look
at.

She was probably trying to endure the heat by stopping her Ice Arts,
preparing for any unfortunate incidents, so she was drenched in sweat.

After a day, two days, and on the third day, she seemed unable to bear it
any longer and suddenly took the seat next to Qing.

Then she grabbed Qing's hand and placed it on her cheek.

"Oing."

What's this? Is this some kind of seduction?

However, Seol Yri was in a state where she had been in a sauna all by
herself.

Sweat dripped from her chin as she pressed someone else's hand to her
cheek, leaving a damp, sticky feeling on the hand.

"If you're going to put someone's hand on you, shouldn't you at least
wipe off the sweat?"

"You said it again."

Qing deciphered the three syllables.

Since her hand was being held, she couldn't avoid getting it damp, so it
didn't really matter if she wiped it or not.

Qing's hands are cold.

The Small Hand Demonic Arts was ultimately the Indestructible Diamond
Body.

When she was at the Late-Stage Peak Realm, it had a weak protective
power, almost like a Plated Indestructible Diamond Body. Now that she
had reached the Transcendent Realm, it had full-front, rear, and side
armor plating that was comparable to that of a Semi-Indestructible
Diamond Body.

However, she lost her warmth in exchange for defense.

But that coldness was a great help to someone exhausted by the heat.

"If you're too hot, you can use your Ice Arts."

"It's dangerous."

"I'm here, you know?"

"A martial artist should protect themselves."

"Oh."

It was the most inspiring thing Seol Yri had ever said.

Indeed, it was not the right mindset for a martial artist to rely on others
just because they could stay cool with their Inner Qi.

However, Qing liked it better when Seol Yri was useless and just existed
as she had been up until now.

If there are a limited number of bad guys in the world, wouldn't my
share decrease if there are more people cutting them down?

"Here. Here you go."

Qing placed her hand on Seol Yri's nape and activated the Ice Arts of
the Lunar Jade Maiden Divine Arts.

Seol Yri shivered once, then soon slouched her shoulders, a soft sigh
escaping her lips.

"Haahhh……"

She seemed to be feeling very good.

She likes it, huh? Then I'll just do it up to here.

She might get spoiled if I do more.

When Qing stopped the cold, Seol Yri looked at her with a somewhat
disappointed gaze.

Qing just pretended not to notice.

Seol Yri didn't ask or demand anything while sending a longing look.
Seol Yri was useless, but she did have some sense of shame.

She also knew how to thank Qing for buying her things. She never
asked for anything herself since she was in a beggar's position, so if she
felt disappointed, she just stayed disappointed.

If Qing offered to rent a room at an inn, they would use it together.

However, if Qing decided to kick her out, Seol Yri would just wait
outside in the rain.

Ah.

Only then did Qing realize something.

That's right. She wasn't even my companion.

Wasn't she just sticking to me like glue because I'm her only clue to
finding that Seol bastard?

Hmm. Well. She's cute, so it's fine.

And even though she's not talkative, she's surprisingly responsive when
spoken to, isn't she?

"Young Lady Seol. It's boring, so tell me about the North Sea. What's it
like there? Is it very cold?"

"I don't want to."

Qing was stunned.

Can you answer 'I don't want to' to the question of whether it's very
cold?

Only after realizing that was an outright rejection of telling her about
the North Sea did Qing understand.

The day was hot and humid, and her hand, still on Seol Yri's nape, was
damp with someone else's sweat.

Qing's irritation level was not low either.

"No, seriously, what's wrong with you? We're traveling together,
chatting, eating together, ah, well, we are eating together. Anyway, do
you not want to talk to me? Do you not want to be with me? Are you just
with me because you have no choice?"

At that, Seol Yri's eyes widened.

Then, with a somewhat forlorn look, she replied.

"That's not it……."

"Then what is it? You don't want to talk to me, do you?"

"No."

"Then what? Do you want to talk to me?"

"No."

Qing's eyebrows shot up.

Then Seol Yri hurriedly added.

"But I don't dislike it."

So she didn't particularly avoid conversation, but she didn't particularly
want it either.

But she didn't want to talk about the North Sea.

Qing glared at Seol Yri.

Seol Yri was always meeting Qing's gaze, but this time she seemed to
avoid it, probably looking at her nose or lips instead.

Seol Yri was such a clueless person that watching her made Qing
reflect on herself.

Is this what that mirror therapy thing is?

As such, Qing calmed her irritation and thought carefully.

Why? Is she embarrassed about her hometown?

Come to think of it, it might be rude to ask if the North Sea was cold.

In Qing's hometown, if you asked someone from the Potato Province (Gangwon)
if they really planted potatoes in their front yard, backyard, side yard,
and everywhere in the neighborhood, they wouldn't react very well.

Later, she heard that it was because they actually planted them, so they
had nothing to say and that made them angry or something.

Or if you asked someone from the Tangerine Island (Jeju) if they had a lot of
tangerines. And what was delicious besides tangerines?

Or if you went to a friend's house who was from a port city and said, 'Wow, you guys have fried chicken, alcohol, and bread too? I thought
you only sold pork and rice soup and buckwheat noodles?'

Something like that.

Hmm. The North Sea must have some merits to it, so she must be living
there.

It might have been a bit rude to just ask if it was cold.

"Hmm. Then is it okay to talk about other things? What kind of food do
you like, Young Lady Seol? You must have a preference, right?"

"Hot things."

"There's more than one or two hot dishes, you know?"

"Hmm. Gruel."

"And?"

Then she shut her mouth again.

Qing's eyebrows rose again.

Then Seol Yri hurriedly answered again.

"I don't know the names……."

"Ah."

Seol Yri was a beggar without a penny to her name.

Moreover, unlike Qing, who was intelligent but lacked dignity,
come to think of it, not just Seol, but also Jegal and Nanah all had
intelligence but no dignity. Among them, Nanah was probably the most
dignified, though.

Except for the sexual harassment.

Anyway, since she was a beggar and had no friends, she wouldn't know
anything about the cuisine of Zhongyuan.

It wasn't likely that she would ask a chef, waiter, or server what the
name of a dish was.

Since she was a woman who just stood in the rain when it rained, she
probably just ate whatever was given to her.

"Sheesh. If you don't know, you can learn. From now on, when you eat
something and it's really delicious, just ask me. You should know the
identity of your favorite food."

At that, Seol Yri blinked.

Then she nodded again.

Anyway, she's pretty, so it's all good. Seriously.

It was when Qing decided to let it go again.

Thump! The carriage shook greatly, then it started to sway left and right,
making the ride very uncomfortable.

"Driver? What's going on?"

"Ah, I don't know. The rain has made the road terrible. I'm trying my
best, but, well. The road hasn't been maintained at all from here on, so
there's nothing I can do."

"Ah. Okay."

What could Qing do when the road was a mess?

The driver wasn't a road-paving expert, after all.

"Just bear with it a little. We'll reach the next village in about half an
hour. It's already past dinnertime and you must be hungry, but it's a
very generous village, so you'll be satisfied. Hehehe."

Thus, while swaying left and right and rocking up and down, the body
was also tilted backward, indicating they were climbing a steep slope.

It was a very bumpy ride that made it hard to even have a conversation
with Seol Yri, so one had to exert some effort just to keep their body
from being flung around.

Of course, Qing had superhuman balance and core strength, so it
wasn't a big deal for her, but…

Seol Yri swayed back and forth, leaning heavily on Qing before being
flung in the opposite direction and banging her shoulder against the
carriage wall. She was practically fluttering like a piece of straw.

Upon seeing this, Qing thought.

No, how can a Transcendent Realm Master not even keep their balance
with a little shaking of a carriage?

Her realm might be Transcendent, but isn't her skill a bit too much of a
fraud?

But Seol Yri was a tracker of the North Sea.

Seol was also not low in realm, and since she was stronger than him,
she was sent to capture him, wasn't she?

Then again, it was a bit strange.

Was it normal to send such a clueless, stupid, and useless kid to catch a
runaway?

Seol also had a low realm when he escaped, but if she couldn't find him,
then what? And even if she found him, was there any guarantee she
would win?

No, wait. Seol also escaped when he was just a trivial First-Rate
nobody.

If she was a Transcendent Realm Master, she would have thought it
was enough to cut off his head and bring it back.

However, if I was someone who worked at the Ice Palace, I don't think
I would send such a useless kid.

She can't do anything, so she's useless. But why would I send her to
track down criminals?

Ah!

Only then did Qing realize the truth.

Maybe she was just idling around at the Ice Palace, doing nothing, so
they sent her to Wulin to gain some experience and become a person!

After all, there was no great danger if she was with the Wulin Alliance,
so they probably told her to learn the ways of Zhongyuan while
she was there.

In any case, even though the carriage tilted and swayed as if it was
trying to evenly coat the passengers inside with flour, the coachman's
skills were commendable as it didn't fall over.

It's a long time since I've felt this uncomfortable.

After what felt like an hour, Qing could hear the sounds from outside
with her superhuman hearing.

-Stop! Ah! Is it Jang? Is it that Jang bastard?

-Hehe. It's me.

-Why are you so late?

-Ah, don't even get me started. The rain made the road terrible. It's a
miracle the carriage didn't tip over. Hehe.

-Well. That's true. Hey, open the door!

It seemed they had finally arrived at the village.

A generous village, huh?

Honestly, it was a bit, not really my thing.

In fact, even if the village had poor hospitality, Qing didn't really care.

She preferred the quality of the cuisine and accommodation over
generous hospitality.

After all, even if the hospitality was poor, it would become generous if
you just paid them. However, even if it was cheap and plentiful, if the
taste was lacking, it just made her feel like she had lost a meal.

As such, the carriage's shaking stopped as it entered the village.

And soon after, it came to a complete halt.

Oh. It stopped already?

It seems like the inn is located right near the entrance of the village.

That's a very good location.

Then the door burst open, and a musty smell spread as soon as it did.

Ah. This is not good. The smell is already like this.

As Qing was expressing great concerns about the quality of the inn, the
coachman urged them to come out.

"We have arrived. You must enter the inn now."

"Are there no other inns? The smell is already quite noticeable. Is this a
good inn?"

It was common for coachmen to receive kickbacks for bringing guests to
certain inns.

So, they brought guests to inns that gave them kickbacks, not
necessarily good ones.

"Aigo. This is a small village, so there's only one inn. Now. It must have
been hard climbing up the mountain path, so you should rest a bit."

"Ah. Yes. Well."

Since there's only one, there's nothing that can be done.

As Qing got off the carriage, she thought, 'Hmm. What's this?'

It wasn't a stable, but a large, what should I call it, this kind of space?

There were no walls, just pillars holding up a roof. A barn? Anyway, it
was some kind of space with an unknown purpose.

A welcoming crowd surrounded the carriage, and as far as her eyes
could see, there were swarthy men with their shirts off, grinning.

"Coachman?"

At that, the coachman quickly ran and squeezed in among the men.

"Hehe, ladies, this is the village of our Green Forest elders, called
Gam3 Mountain Stronghold. Since dinnertime is approaching, the
elders of the Green Forest will feed you until your stomachs burst, so
after today, you will be full for the next ten months. Hehe."

At that, a large man slapped the coachman's back and burst into
laughter.

"Look at this bastard talk. He says you'll be full for ten months. Hahaha,
that's why I like this Jang bastard. Yes, the goods are indeed
exceptional. Wow, they are truly the most beautiful women under the
heavens."

Only then did Qing realize the situation.

I thought it was strange that this coachman didn't try anything funny.

Turns out he brought us to a mountain stronghold in a carriage.

Ah. I should have realized something was off.

What kind of village is located at the top of a mountain, where you
have to climb a winding mountain path?

Villages are usually located near water at the foot of a mountain!

Or they are fortified at around the middle of the mountain to avoid
government taxes.

I was too busy watching Seol Yri sway and stagger to think of anything
else, but now that I think about it, it was quite strange.

Coachman, you bastard. How could you do this to me……!

If you had just told me in advance, I would have been looking forward to
it.

What's this? Is today my birthday? Or Buddha's birthday? Or that
foreigner's birthday?

Is today Christmas or something?

Why? Among all the movies, there was that one called July, no, was it
August?

Anyway, what a surprise gift.

This is so, so, so thoughtful of you. I'm so touched. 