\chapter{Journey to Zhongnan (9)}

It was an utterly unexpected ambush.

Despite being an ambush, the Lulin Fort Chief was killed in a single
blow.

The cruelty of the attack made everyone present hold their breath.

A moment of silence descended, and the sound of the pouring rain
became loud. But soon, it was broken by someone's shout.

"Damn it! Young Master!"

See?

The first thing they're worried about is their precious Young Master,
huh?

Qing's head whipped around.

The eyes looking at the Young Master were full of malice.

The man who shouted realized his mistake.

Originally, when someone was being guarded, the moment something
happened, they should be immediately and inconspicuously hidden
away. Only after that should one worry about eliminating the danger.

But no matter how high one's realm was and how much experience one
had, a mountain bandit was just a mountain bandit.

How could they know how to protect someone when all they knew was
how to steal?

"Wait! I am the Vice Chief of the Black Wind Triad Branch."

"I didn't ask!"

Qing's figure shot forward once again.

The Hellish Demon-Slaying Blade, which drew a long tail, was blocked
by the blade of a hand ax on its waist.

To block the ferocious charge of the Hellish Demon-Slaying Blade,
which was imbued with Sword Force, one had to at least be able to
surround themselves with Sword Force. And the Vice Chief did just
that.

Kwang! Despite the sound of weapons clashing, a huge explosion
resounded.

Qing shouted fiercely.

"Why does everyone and their mother use Sword Force?!"

"Wait! Stop!"

"If you're going to suggest resolving this through conversation now!"

Qing extended her foot once more. It was because the sensation of
crushing a hard shinbone with the tip of the foot was truly exhilarating.

However, the Vice Chief had already seen it with his own two eyes.

He widened his legs awkwardly, barely brushing past Qing's toes.

But Qing did not give up.

"It's already!"

While in that state, Qing suddenly raised her knee and leaped. Her
knee was aimed at his chin. The Vice Chief performed an Iron Bridge
technique, leaning back to avoid the attack aimed at his chin.

"Too late!"

Qing straightened her knee and extended her leg.

The sight of Qing's legs, straight as an 'I', standing upright on the
ground was astonishing. But only for a moment, as Qing's raised foot
plummeted to the ground like a falling meteor.

The Vice Chief hurriedly rolled, abandoning all dignity and desperately
trying to escape.

Kwoooong!!

Black Demonic Qi surged from the ground like a wave, swirling around
Qing before dissipating.

Second Stance of the Heavenly Demon's Advent Steps.

With each step forward, it summons a gust of wind.

A single step, a wild gale.

"Keoheok."

The Vice Chief groaned while lying down.

He had barely avoided being crushed, but his entire body was exposed
to the Heaven-Shattering Demonic Qi that had spread through the
ground.

But there was no time to be in pain.

After all, there was a reason why humans had two feet. It was to take
turns stepping forward and moving onward.

"You roll well!"

Qing roughly pulled her knee back.

At first glance, the action looked ridiculous, but the aftermath was
never a laughing matter, as he had learned firsthand.

Once again, Kwang.

The Vice Chief rolled away, barely dodging.

"Wait! Stop! The Young Master!"

"I told you I'm not interested!"

Qing had simply decided not to listen.

What did it matter whose Young Master he was when he was going to
die anyway?

And so what if he knew?

Who's not a precious daughter?

Besides, he's not gonna be a princess, is he?

The blade of Qing's sword surged with Sword Force.

The continuous strikes, which involved hitting, swinging, stabbing, and
twisting, seemed clumsy at first glance, but it was a strange technique
that did not allow for any counterattack.

"Wow, what's this? You're pretty good at fighting, Mister. Why are you
even a bandit? Ah. Is it because of something like that? You were born
as a son of a bitch, so you can't stand not doing shitty things?"

"Damn it, what are you doing! Protect the Young Master!"

"Fuck off!"

Qing's swollen right hand stretched out smoothly, then, Deeeeng!
The Resonance Palm of a Transcendent Master slammed into the
Young Master's shin.

There was a splash of blood as the white rear part of the shinbone was
revealed.

"Aaaaargh!"

The Young Master collapsed to the ground, and the bandits rushed
towards Qing, with some trying to protect the Young Master.

Ah. Right. What about Young Lady Seol?

Qing hurriedly looked for Young Lady Seol and saw the silver-haired
girl running away with her back to Qing.

Wow. She's running away without even looking back.

No, wait. That's actually better.

It would have been a burden if she had just lingered around, trying to
help, only to get caught. Even if she didn't get captured, it would be
pitiful if she got cut by a stray knife in the chaos.

Hyeop! Qing shouted and threw the heavy blade with both hands.

The blade spun ominously through the air.

It penetrated the shoulder of a bandit who was supporting the Young
Master and stopped when it reached the middle of his spine.

As a result, the body that used to be a bandit fell to the ground, and the
Young Master, who was right beside it, also fell.

Then, a powerful gust of wind blew from behind.

With her Energy-Sensing Divine Arts, Qing could grasp what was
happening within two cheok around her body without even looking.

Qing twisted her body to avoid the attack from behind and grabbed the
wrist of the attacker, twisting it lightly as if breaking a piece of
straw.

Snap.

Aaaargh, came a scream from the new weapon.

Qing swung the attacker by the neck and waist, and the bandits
couldn't dare to swing their weapons, thus hesitating.

Then, Qing threw the attacker, causing the muscular weapon to
collide with the bandits, resulting in a loud crash.

And finally, the Moonlight Sword!

With a sword in hand, Qing, moving among the bandits, was like a fish
that had met water.

Every time the sword swung, a neck would get lopped off. Arms and
legs would get severed, too. If it didn't get cut off in one go, one had to
question whether the Sword Force was lacking.

Then, one could see the Young Master quietly trying to escape with
the help of a thief.

Deeeeng! A Resonance Palm strike, and the thief's mouth spewed
blood as he collapsed, with the Young Master rolling on the ground
beside him.

The Young Master, with his shinbone exposed and tattered, screamed
at the top of his lungs as it hit something.

"Wait! Stop! That person is the Chief's……!"

"Ah, fuck. So much unnecessary information! I'm not interested!"

Even so, the Vice Chief tried to reveal the Young Master's identity
whenever he had a chance, so Qing was getting too busy to even have
three bodies, let alone just one.

Of course, even if she did have three bodies, only one out of the three
would be able to enjoy, so she didn't particularly want that either.

The Vice Chief was going crazy.

He should have fled long ago.

But the problem was that he had no way out.

He would die here anyway and if he failed to protect the Young Master,
he would die. In fact, the latter would involve a long period of
excruciating torture before begging to be killed.

"Damn it! Kill her! Attack all at once! Do you want to die by my hand?!"

The Vice Chief shouted, wielding a deep blue Sword Force. In response,
the bandits charged at Qing all at once.

Blades and axes poured in from all sides, shining brilliantly.

Qing's eyes flashed, and she took one step forward, then two,
crouching and pulling the sword back.

Paaak! Puk! Pak! Her back, shoulders, and sides felt as if they were
being seared with a hot iron, causing sparks to fly in her head.

But she endured it!

After all, Qing's muscles and bones were too tough and sturdy for such
crude attacks to damage, and above all, she had the Protective Qi she
had learned in the form of a mental patient with exhibitionism from
the Divine Maiden Sect.

Thus, the sword extended.

From Qing's hand, in a straight line, piercing the Vice Chief's heart and
out from his b.a.c.k.

"Keo, heok."

Qing's lips formed a sadistic arc.

The blade of the Moonlight Sword (No. 8) twisted half a turn and then
rotated in the opposite direction.

Kureuk, blood gurgled out from the Vice Chief's mouth. It was full of
agony.

Seeing the Vice Chief's agonizing face, Qing's heart bloomed like a
spring day's canola flower.

But wait, hm? This is strange.

It's definitely fun, but not as much as I expected.

Originally, at this point, after seeing and feeling the tearing of flesh
and bone, there should be a certain craving rising from deep within.

That's why I used to act more cruel.

But this time, it's just somewhat enjoyable?

Of course, it's fun.

Well. If it's delicious, it's good, and if it's fun, then that's great too.

At this time, in Qing's dantian, the True Qi of the Daoist and Buddhist
schools clapped their hands together, raised the Blissful True Qi into
the air, and cheered while spinning around in circles.

The solitary star of Heavenly Slaughter smiled benevolently at the
scene.

And the Heaven-Shattering Demonic Qi was also smiling.

After a while, the Blissful True Qi, which had been flying in the air,
suddenly swooped down and slammed the giggling Heaven-Shattering
Demonic Qi.

As soon as the fight broke out, Seol Yiri immediately turned away from
Qing.

However, this was not an act of escape, running away, or what was
tactically referred to as a 'reverse charge'.

She was simply following the basics of warfare, which stated that one
should seek out an advantageous battlefield.

The Ice Arts were not regarded highly for various reasons.

First, its power did not come through when it was hot.

But when it was cold, the power did not come through either.

This was because people were prepared for the cold during cold
weather.

They wore undergarments with fur and thin clothes, as well as thick
padded clothing on top.

The practitioners of Ice Arts often said that its power was actually
stronger in summer than in winter.

At least in summer, one could immediately strike the cold into the skin
or thin clothing.

It was actually harder for the power to manifest in the cold winter.

However, there was a time when practitioners of Ice Arts could go
crazy, and that was when it rained.

To be precise, it was when the enemy was soaking wet.

In winter, even if it rained, the clothes were thick, so it was rare for
them to get completely drenched.

But when Ice Arts were unleashed during a summer downpour, its
power was finally unleashed. After all, it froze upon a mere touch,
starting with frostbite at the very least.

Thus, when the bandits chased after the beauty, thinking she was
fleeing, and the beauty took her place outside the roof and turned
around, and when they saw two ice dragons emerging from both her
arms with the sound of ice clinking, they thought to themselves.

Ah. This is a bit too much, isn't it?

However, whether it was too much or not, Seol Yiri, now facing her
enemies, charged forward.

As the distance narrowed, a bandit hurriedly swung his ax, but Seol
Yiri, who had already stopped just outside the reach of the ax blade,
could not be hit.

Instead, she extended her right arm, and the Right Ice Dragon coiling
around it opened its maw and bit the forearm.

"Aaaargh!!! Uh?"

The bandit, who had screamed in pain, made a puzzled sound.

It definitely felt like he had been bitten!

There was no pain, only a strange sensation of coldness and heat
remaining on his forearm.

But only for a moment. Seol Yiri's palm struck his forearm. It was the
Ice-Shattering Palm of the Northern Sea Ice Palace.

Since half of his forearm was already frozen solid, it shattered into
pieces, scattering bright red ice fragments in all directions, revealing
the white bone underneath.

"Aaaaargh!!! Eok."

This time, the bandit screamed properly.

However, it did not last long. After all, one cannot scream when a
blade is lodged in their mouth.

A long, transparent rapier protruded from the back of the bandit's
neck before retreating back.

A thin ice blade, about a finger's width, emerged from somewhere and
was soon held in Seol Yiri's hand.

Once again, the Right Ice Dragon emerged, naturally coiling around
the blade.

It was the Northern Sea Divine Art, Ice White Divine Palm. And the Ice
Spirit Divine Sword. 