\chapter{Journey to Zhongnan (8)}

The bandits of the Greenwoods were the masters of all mountains.

At least, that was what they claimed.

It was a statement that would make the Emperor, the owner of all lands in Zhongyuan, scoff in disbelief. However, since he was too noble a figure to be angered by the words of lowly bandits, there were not many instances where he actually launched a suppression.

Unless they dared to mess with the government's goods, the authorities would not waste military force on such trivial matters.

After all, the soldiers of Zhongyuan were imbued with the grand ideology of protecting the Central Plains.

They were a military force far too precious to be mobilized for something as insignificant as maintaining public order.

In the first place, public order was something that involved those filthy commoners, who reproduced and multiplied like vermin, so neither the Emperor nor the authorities had ever been interested in it.

If the authorities had suppressed the bandits even half as much as they had oppressed and exploited the martial artists before the era of the Celestial Martial Emperor, the Greenwoods would not have prospered as it did now.

But this was the will of the authorities, as well as the will of the Emperor.

Even if the Shaolin Temple dared to help the commoners, such an act would be deemed as a grave treason, deserving of punishment by a rain of cannon fire. On the other hand, a group of bandits harassing the commoners was an insignificant matter that could be overlooked.

If Qing had been interested in the history of her homeland during her previous life (although there was not a single person in the world who was), she would have known that the leaders of China had been unusually lenient towards bandits.

However, Qing was unaware.

She was ignorant of not just the history of Zhongyuan, but even the current history of Wulin.

But this ignorance was actually quite normal, because ordinary people did not have an interest in history.

At any rate, the bandits of the Greenwoods thrived on the government's indifference and the blood and tears of the commoners.

Even when the authorities were powerful, they were not suppressed. And after the era of the Celestial Martial Emperor, they had the time of their lives.

Thus, the current state of the Greenwoods was at its peak in all of its history.

So what exactly was this Greenwoods?

If Qing knew about the Greenwoods, she would have thought of the franchise concept of her homeland.

There was the main headquarters called the Main Stronghold of the Greenwoods and the direct branches called the Eighteen Strongholds of the Greenwoods.

And then, if other bandits paid money to the Main Stronghold of the Greenwoods, they were allowed to use the name of the Greenwoods.

These strongholds that just borrowed the name of the Greenwoods could be considered as independently managed stores.

And then, once every few years, they would line up according to their achievements. The top fifty-four would receive a special signboard and a dispatch of Masters from the Greenwoods to provide martial arts instruction, as well as various other benefits.

Thus, the Eighteen Strongholds, in addition to the top fifty-four strongholds in order of merit, were called the Seventy-Two Strongholds of the Greenwoods.

However, since merit was determined by the ones who assessed it, there were several strongholds that somehow made it into the ranking without offering any special tribute, often ranking quite high.

And on the stronghold of Gamsan, there were two signboards. The one below said Gamsan Stronghold, and the one above was a grand signboard that read, 'The Twenty-Ninth Stronghold of the Greenwoods, the Lord of All Mountains Under Heaven'.

But Qing never saw it.

Since she was whisked away in a carriage, she never saw the fully fortified stronghold. As such, she had no idea what kind of signboards were hung.

Of course, even if she saw them, it wouldn't have made much of a difference.

So all Qing could think was…

What's this?

Why do these damn bandits all know martial arts?

From the looks of it, they are at least Second-Rate, since they all have Inner Qi. They're almost on the level of a combat unit. Why would people like them become bandits?

"I am Bak Sal, the Great and Mighty Chieftain of Gamsan Stronghold. Although I regret to have to meet you Young Ladies like this, may I ask where you are from?"

How can someone's name be Bak Sal1?

But then again, bandits often abandoned their given names for stronger ones.

Bak Sal had changed his name to Bak Sal and was very pleased and proud of it.

"What business do you have knowing, you fucking highwayman?"

Why is he trying to make conversation when he has a perfectly good sword?

How ridiculous.

Qing shot back.

"Can't you see what's going on here? Do you think you're in a position to be acting so bold right now?"

Bak Sal had been expecting the two beauties when he was contacted.

However, when he saw the two who got off the carriage, he thought, 'These are some seriously beautiful women.'

"Why are you so full of yourself? Don't know how some pieces of trash who only harm the world are still breathing. If it were me, I would have bitten my tongue off and died rather than live as a bandit."

At that, Bak Sal's blood pressure rose slightly.

And there was one whose blood pressure rose significantly.

"You bitch, you're just a bit pretty, so I was gonna go easy on you. How dare you talk about the great Greenwoods like that in front of us?! Do you want your slit torn apart?"

He was a young man about Qing's age.

Qing glanced over the young man and immediately found a spot that would hurt the most.

"What's with this little shit? Mind your elders when they're talking and go to sleep. You need a lot of sleep to grow, and it seems like you need a lot. You're so short for a man."

"Wh-What?! You bitch, I'll-"

"Ah, Young Master. Please calm down."

At that, Bak Sal held back the young man and bowed.

Qing's eyes flashed.

What, Young Master? Is he some big shot?

He's a big shot, but he's in cahoots with bandits?

Not only does he have a lot of Evil Karma, but now there's an additional reason to find him detestable.

How should I kill him so that it is known that I killed him well?

Meanwhile, Bak Sal felt a sense of foreboding.

Excessive beauty was a symbol of a prestigious family.

Prestigious families were basically composed of handsome men and beautiful women who had been together for generations, so their appearances were naturally extraordinary.

Moreover, for her to be so bold in this situation meant all the more…

Qing read Bak Sal's eyes.

That guy's rolling his eyes. It seems like he's quick-witted. If I just smash his head in with the Buddha's Palm, the rest will-

"I am Seol Yiri of the North Sea Ice Palace."

Seol Yiri suddenly spoke up.

Unlike Qing, who was itching for a fight, Seol Yiri found this situation to be quite burdensome.

"Ice Palace? The North Sea Ice Palace? Then, this bitch is?"

"I am a disciple of the Divine Maiden Sect, Ximen Sojeo."

"Oho. I see."

The young man let out a sinister laugh.

"Hah. To think that there was a Plum Blossom, one of the Five Flowers of the Martial World, from the Ice Palace here. And next to the Divine Maiden Sect, no less."

"Young Master? Please calm down for a moment-"

"Indeed! Shouldn't a man at least try to have one of the Five Flowers of the Martial World under him at least once! Don't you think so?! Fuck, today I'm going to fuck all the holes!"

"Uoooooh!"

At that, the bandits of the Greenwoods all roared in unison.

From the start, the coachman had brought them here knowing that they were foolish and easy women.

Since no one knew that they were heading for Gamsan Stronghold, they could do whatever they wanted with them until they died and no one in the world would know.

Even the Nine Sects One Union and the Ten Noble Clans wouldn't bother searching for missing people too hard, so even if they did, they wouldn't dare to touch them out of fear for what would come after.

But the Divine Maiden Sect and the North Sea Ice Palace?

The Divine Maiden Sect was a mysterious sect full of peerless beauties, but they were not particularly dangerous. And what could those from the Ice Palace, stuck in the far North Sea, do about it?

Moreover, their dicks were already hard, so there was no turning back.

Sadly, the fate of men was to follow the will of their dicks rather than their brains.

Besides, when would they ever have the chance to have one of the Five Flowers of the Martial World beneath them?

Moreover, the bigger woman next to her, though tall, was even more beautiful. It was no wonder, to think the Divine Maiden Sect, that sacred realm where only men were forbidden, had hidden away such a beauty that could surpass even the Five Flowers of the Martial World.

Even at the risk of death, it was worth a try. If they let this chance slip by, they were no longer men.

The young man spoke proudly.

"That's right. It's ten."

However, Seol Yiri, who had said all she had to say, shut her mouth, and Qing didn't reply because she was watching the situation with bated breath, hoping it wouldn't fall through.

As such, no one asked what he meant by ten.

The young man cleared his throat and spoke again.

"Each of you, have five babies. Then I'll let you go."

At that, Qing felt relieved.

Because of this useless bitch, I thought it was going to fall through, but it seems like we've come to a conclusion to fight.

"Young Lady Seol."

"Yes."

"If you think you can't handle it, just run away immediately. I have the ability to escape from anywhere, so you just have to take care of yourself. Got it?"

As Seol Yiri nodded, Qing's foot stomped the ground.

Kwang!Yellow True Qi created a circular wave.

The ground, firmly packed, was dented as if it had been hit by a cannonball due to the terrifying True Qi.

Qing was fast.

Her inherent leg strength, as well as her physical specs, were far beyond human. And when such monstrous strength was combined with the mysteries of the universe, martial arts, the result was no different from the transfiguration described in stories.

Bak Sal was startled when Qing suddenly rushed before his eyes the moment he heard a loud bang. As such, he hastily drew his saber.

As the leader of a regular stronghold, Bak Sal was a Transcendent Realm martial artist. Even though he was startled, his body immediately reacted and responded.

Thus, a deep blue Saber Qi formed and drew a straight line from the sky to the ground.

Qing's hand reached out and slipped in between.

Since he didn't expect her to grab the blade covered in Qi without any hesitation, Bak Sal put more of his sinister energy into it, determined to blow all her fingers off.

However, with a thud, the saber covered in Saber Qi touched Qing's palm and stopped.

Bak Sal was surprised and looked at Qing's hand, finally noticing the sunset-colored Hand Qi covering it.

Qing was a beauty, and also a young girl who looked like she had just turned twenty. Judging from her age, he never imagined that she could use Force Manifestation, so the moment he saw it, he realized he had messed with the wrong person and-

"W-Wait a moment!"

"Sure!"

There were three reasons why Qing replied so vigorously.

First, with a kick to his shin.

Second, with an upward strike to the cheek with her palm that had just descended to his bent waist.

Third, with the hilt of the saber that was lifted up vertically.

Crack, a sweet sensation of destruction. Ah. Seriously. This is why I live.

The long hilt of the saber, long enough to be held with both hands, was driven into Bak Sal's skull.

As Qing pulled it out, whitish-red things oozed out with viscous strands.

Qing roughly wiped it off with her other hand and firmly grasped the saber with both hands.

"Well! Cry out! Infernal Demon Subjugation!"

The Yue Maiden Sword's Sword Sutra was unleashed from Qing's hands.

It didn't matter if the shape, size, or weight of the sword was different. Even if it was held with one hand or two hands, it was still a sword in her hands.

A broad saber was swung horizontally with both hands, turning with her waist, creating a fierce whirlwind that caught two bandits.

Their upper bodies, neatly cut above the solar plexus, fell to the floor with a thud. The four arms that were cut below the shoulders also fell to the floor with a thud, thud, thud, thud.

It happened in an instant.

Only then did the bandits of the Greenwoods realize what had happened.

They hadn't caught the wrong prey.

Rather, they were about to have their bodies pierced by the blade of someone they should have never messed with.

It wasn't the chance to mount peerless beauties however they wished, but rather that their own bodies were about to be mounted by blades.