\chapter{Journey to Zhongnan (10)}
Baksal, the Great Forceful Tiger. Heukpungsamjeolbu, the Black Wind
Triple-Axe. Gansoju.

When one reached the Transcendent Realm, their titles were known far
and wide. As such, they were not people who would be stuck in a small
mountain stronghold.

However, Gamsanchae was not a small mountain stronghold.

After all, it was an inland base of Nokrim.

There was no commerce route above or below Gam Mountain due to the
river, so it was an ideal location to avoid the attacks of the Shaolin
Sect to the right and the Mount Hua Sect to the left.

Therefore, Gamsanchae was not a mountain stronghold for bandits'
main purpose, which was robbery.

Instead, Gam Mountain was located in the west of Henan, which was
around the center of the world.

Furthermore, it was the starting point of the mountain range that
stretched to Shaanxi Province, Shanxi Province, and the western part
of Hubei Province in order from the north, west, and south.

As such, it was an important base for reserve forces scheduled to
rotate, as well as for patrolmen and dispatched agents of Nokrim.

It was a midway base that the main base assigned a number to since it
wasn't one of the Eighteen Outer Strongholds, due to the fact that there
was almost no business as bandits. But at the same time, it was also too
important to entrust to someone else.

In the first place, it wasn't a common mountain stronghold to begin with,
as there was a martial artist of the Transcendent Realm acting as the
branch manager when it wasn't even a directly-managed branch.

However, Qing was in no position to have such high-level thoughts,
draw conclusions by gathering clues, or have any interest in such
matters to begin with.

What do I care.

To think there's two Transcendent Realm Masters here.

There really are a lot of Transcendent Realm Masters in the world.

In truth, it was quite common to see Transcendent Realm Masters.

If it was a city of intermediate scale or larger, there was at least one
taking up a position somewhere.

It was a realm that could be reached before death if one had proper
martial arts, the diligence to train consistently, and the ability to live
long.

One could say that it was practically the highest level that could be
realistically reached by martial artists who had no particular talent, no
backing, and no Divine Arts.

This was because the overall level of martial arts always went up,
continuously rising as time passed.

So if a society as advanced as Qing's hometown was to form in the
future, it might be possible to graduate from high school after achieving
the Transcendent Realm.

At any rate, after the Masters they had trusted like the sky suffered a
series of defeats, the morale of the bandits plummeted, so much so that
it pierced through the ground.

Above all, they had completely lost their will to fight from that vicious
method where they got beaten up and down, left and right, before
finally having their swords extended towards them.

After all, when a person who had been hit by a mace and an axe was
standing perfectly fine while smiling, the bandits could no longer see
them as a human being.

"M-Monster……!"

A monster has appeared!

Chuckling, Qing drew Moonlight Sword (No. 8).

Of course, following Qing's principles, the sword that entered through
one way had to exit through another. And now that she had Sword
Force, she could neatly create a path from top to bottom. As such, the
sword that pierced the heart exited through the top of the head-

Wow. This actually works!

As such, at the gruesome sight of a person being split in half from the
inside, the bandits panicked and immediately turned to flee.

"Where do you think you're going!"

Binyeos flew, but with the bandits scattering like cockroaches in all
directions, Qing only had two hands and a limited number of binyeos.

Tsk. You should know you're lucky.

Qing hurriedly moved around, taking care of those who had fallen after
being hit by the binyeos.

She would step on their spine, puncture their lungs so that blood would
pour into them, or even slit their stomachs to expose their innards.

In common, she was going around and inflicting fatal wounds that
wouldn't lead to immediate death but were very painful and would
eventually result in death.

If one thought about it, this could be considered an extremely merciful
act for Qing. It was just that while it was fun, her heart didn't race and
she didn't feel that tingly thrill.

Why is that? It's nice that my mind is clear, though.

Thus, Qing finally approached the young master who was crawling on
the ground.

Clack! Clack!

It was unclear how those footsteps could be heard from the ground,
even though it was just soil that had been firmly packed.

However, as the young master crawled away desperately at that sound,
Qing leisurely took one step at a time, following him. Clack, clack.

"Well. Young Master? Are you going to keep running away?"

"D-Do you know who I am!"

"I don't know."

"I am-."

"Shhh. Young Master. If you tell me that, I would really be forced to kill
you with tears in my eyes, judging the situation on a grander scale. Are
you sure you want to reveal your identity?"

"Hiiiek. P-Please, spare me……. What do you want? If you spare my life,
wealth, women, and everything-."

"Hmm. For starters, how about some manners? What's with the
informal speech from someone so much younger than me? Can't you
see I'm trying to help you out here? Even when you're this close to
dying, you can't get a hold of yourself? If you beg me politely, I might
consider it."

"Please spare me!"

"For now, try to escape. I'll see how far you get, and if your efforts are
commendable, I'll consider it."

At that, the young master crawled desperately.

Qing followed him, going clack, clack.

Whether it was a stable or a roofed shelter, the young master finally
crawled out from under the roof.

Shoooooo- The rain, which one could only describe as fucking
annoying, instantly soaked his body. As such, the blood from his
exposed, bone-showing calves mixed with the muddy water and spread.

And over there was-

"Eh."

Qing frowned.

The sight of Seol Riyi being dragged by her hair came into view.

In the distant past, in order to complete the Lonely Swallow Seeking
Nothing, the Celestial Martial Emperor wandered all over Wulin.

This included the Ice Palace, so when the Celestial Martial Emperor
saw the peerless Divine Art of the North Sea Ice Palace, he expressed
his thoughts.

It's pretty trash.

Although its power was maximized in the rain, the extreme cold of the
Icebound Divine Palm inflicted frostbite, severely worsening the
aftermath.

Of course, the aftereffects were beyond ordinary. Even if it was cured, it
took at least half a year to recover. If frozen properly and not treated
quickly, the flesh would rot and require amputation, causing permanent
damage. As such, it was quite a vicious technique.

However, just because the flesh froze did not mean that the enemy was
immediately incapacitated.

In fact, according to Western medicine, during battles that determined
life or death, the best combat stimulant was naturally synthesized and
secreted. As such, it made one forget the pain, made the heart beat
faster, and greatly enhanced the body's reaction speed.

It could make one disabled after the battle, but the lethality during
battle was somewhat lacking.

In Qing's hometown, it was the type that was dirty to deal with as an
enemy, but pretty useless as an ally.

At first, the bandits had shrunk back at the visual stimulation of two ice
dragons descending. But after being hit a few times, they went, What's
this? It's hot and cold at the same time?

Is this…… it?

Moreover, the Vice Captain was a Peak Realm Master and had taken
his place at the very front.

"It's all just appearances, don't be fooled! She can't kill anyone with
that! The Young Master must have her, so don't leave any sword marks
and subdue her!"

Although the Young Master was currently crawling on the ground.

However, since Qing had thrown binyeos at the guys who tried to run in
the Young Master's direction, a counterattack from the stragglers was
blocked.

As such, news of the main camp's destruction had not been delivered.

Thus, the bandits regained their courage and rushed in. Seol Riyi
slipped and slid with the footwork of the North Sea, but was hit in the
back with the blunt side of a mace! As such, she staggered.

Then, kicks, maces, and axe handles flew in, asking for a handshake.

Thus, one of the Five Beauties of Wulin, beaten to a pulp, was dragged
back by her hair through the muddy ground.

"Y-Young Master!"

At that, Qing urgently moved, grabbing and lifting the Young Master's
head by the hair.

Head for head. One could call it a form of mirror therapy.

But then, the Young Master resisted, waving his arms.

Qing crushed that insignificant resistance with just one hand.

From the middle of his forearm, it drooped like a willow branch, which
was a bit funny.

Oh, doesn't it also feel a bit like a mantis?

While thinking so, Qing shouted at once.

"Return Young Lady Seol! Otherwise, the Young Master's life is forfeit!"

The Vice Captain was momentarily dumbfounded.

Kidnappings were a specialty of bandits.

Even so, he had lost the initiative.

It was something that damaged his pride as a bandit.

"If, if you even touch a single finger of the Young Master, this bitch's life
is also forfeit!"

"Ah. No!"

"Keuheuk. Hand over the Young Master and drop your weapons before
kneeling. Otherwise, what are you doing……!"

The Vice Captain panicked.

After all, who would panic at the sight of a woman plucking off
someone's fingers right in front of them?

"For now, I have returned one finger. Would you like to return Young
Lady Seol now? Is one finger not enough? Then, one more-."

"Stop! Stop! Stop it!"

"Ah. Then please speak quickly. It's a shame since there's only ten of
them. Here. Since we've already separated it, I'll be generous. I'll give
you one more."

One finger flew in a parabola and landed in front of the Vice Captain.

It was so precise that it even landed on the previously fallen finger,
causing two white fingers to sit in a puddle of blood-tinged rainwater.

"Young Master. It seems like these people don't value you all that
much. They are doing things like starting a hostage situation. What
should I do? If this keeps up, I think I might have to kill you. Do you
have any last words?"

"Let go! You bastards, let her go!"

"But Young Master……!"

"Do as you're told! Baksal and So Sick are both done for!"

Kuhk. Qing burst out laughing.

Baksal is done for because he got baksal-ed1. It's like his name predicted
it.

Or did I do that?

At that, the bandits' shoulders slumped.

To think the Captain and the main base's Master were defeated.

And by that young woman?

"Now, now. It still seems like you're not desperate enough. It can't be
helped. I'll be generous today."

As Qing grabbed the fingers again, the Young Master screamed as he
convulsed, even though it hadn't even been pulled off yet.

At that, the Vice Captain shouted.

"Stop, stop! Here, we let go! We let go, so stop! Please!"

"Alright. Send Young Lady Seol over here."

"A simultaneous exchange, no, an exchange of hostages, no, that's not
it…."

It seemed the uneducated bandit was struggling with using honorifics.
Qing nodded.

"Sure. Hostage exchanges require mutual trust. But we aren't exactly
people who trust and believe in each other, right? Hmm. Then, let's do it
like this."

"Like what?"

"Every time I count, I will remove one finger and send it to you. After
all the fingers are gone, I'll start slicing off bits of the palm, wrist, and
forearm, so you can reassemble it later for treatment, right? I will keep
counting until Young Lady Seol comes into my arms."

"Let go! Release her! ARGH!"

"One."

A finger drew a parabola.

The Vice Captain finally realized the truth.

This is an absolutely crazy bitch!

It could be said that he had accurately grasped the essence with an
insight that was unbelievable for a bandit.

If Qing had known, she would have acknowledged him as the most
intelligent among the bandits.

"Stop, stop! Here, we let go! We let go, so stop! Please!"

Qing's new concept hostage negotiation worked splendidly.
Qing grinned.

I was also talented in hostage situations?

"Hmm. I won't be a bitch and keep counting until she comes into my
embrace. Young Lady Seol? Are you okay? Can you come here?"

Seol Riyi, who had fallen onto the muddy ground, struggled to get up,
staggering and repeatedly falling in an unsightly manner. Eventually,
she just crawled on all fours, staggering and falling again and again.

Qing strode forward and held Seol Riyi's body, embracing her.

She was able to escape, but she ended up like this.

There's no fucking use for her anywhere.

At least her face is fine.

If her face was ruined too, she would have been completely useless.

"It can't be helped. Take the Young Master with you."

As Qing spoke, she picked up Seol Riyi and headed back under the roof.

Then, she carefully put her down.

"Young Lady Seol? Wait a moment. Hmm. Do you need revenge? Should I
capture a few alive for you?"

"Yes……. Please, if you would."

It was Seol Riyi's first request!

Normally, she would just go with the flow. If there was no food, she
wouldn't eat, and if there was no room, she would sleep outside in the
rain. It was the first time she had ever asked for anything.

It seemed like she was that angry, her resentment that deep.

Well, yeah. If someone isn't vicious, then they aren't a martial artist.

It would be stranger if she didn't have a side that I liked.

Qing ran out again.

Fortunately, they were still there.

One might ask if they were stupid for not running away immediately,
but the Young Master's condition was such.

His calves showed bone, both forearms drooped powerlessly from the
middle, and three of his fingers were missing.

He had also lost a lot of blood, so his complexion was pale.

Thus, the Vice Captain had urgently stopped the bleeding by sealing his
blood points and was in the middle of making a stretcher with the
remaining subordinates.

Above all, Qing did not expect that she would change her mind and
return.

Since she had returned the hostage, it included an unspoken agreement
not to touch each other until she left.

That was the general common sense of Jianghu.

However, Qing lacked common sense.

To be precise, she also lacked non-sense.

Thus, Qing, who reappeared, shouted as she raised her voice in anger.

"How dare you make Young Lady Seol into such a state! She was already
useless to begin with! And now she's become a useless patient to take
care of! I absolutely cannot forgive this!"
