\chapter{Journey to Zhongnan (5)}

However, Seol Ri-ri was not a coachman.

After all, being good at driving a carriage did not make one a coachman; a coachman was fundamentally someone who knew the roads well.

In any case, Seol Ri-ri, who was unfamiliar with geography, simply followed the road.

Moreover, it was pouring rain, a situation that was perfect for getting stranded.

Fortunately, it was not easy to get lost in the middle of Henan Province.

Thus, following the road and taking the main paths at intersections, they eventually came across a small village called Bubuk Village.

It was a humble village with only a single inn, but any port in a storm.

Moreover, it was a great fortune that it was not a fortified rural village, considering it was right along the main road.

Thus, after securing a room, wiping their bodies with warm towels (hot water baths were a convenience only available in cities), and buying dry clothes from a waitress for an extra fee since there wasn't even a clothing store in the village…

After a generous meal of a somewhat ambiguous level that could barely be called cuisine, they lay down on a not-so-comfortable bed, and wow, were they tired.

The bed was a bit uncomfortable and smelled a bit musty, so she was still in her right mind. Otherwise, she would have fallen unconscious the moment she lay down.

But why am I so tired……?

Is it just because of a little sword fight?

As Qing lay sprawled out, feeling unusually tired and sluggish, Seol Ri-ri stood there blankly, looking down at her, who only had her head sticking out of the covers.

"What are you doing? Aren't you going to sleep?"

"I can't sleep if someone's around."

Seol Ri-ri's pronunciation had also improved tremendously, so it seemed like she would be completely fine tomorrow after a warm, good night's sleep.

Originally, even a mild cold would be cured in just a day for a Master, no, even for an Intermediate-level martial artist.

In any case, it seemed like Seol Ri-ri was refusing her duty as the last and most manageable reason to keep her around, a human-sized hugging pillow.

"Hmm. Fine. Then let's do this."

"Do what?"

"I think Young Lady Seol can sleep really well even if someone's there. Like, to the point where you wouldn't even notice if someone carried you away."

"No, I can't."

"Alright. If Young Lady Seol can stay still for one gak1 without falling asleep, I'll get another room. But if you can't and fall asleep? Then, since you lied, you'll have to sleep with me from now on, no matter what. How about it?"

"I don't want to."

"Then sleep on the floor or something."

"That's mean."

"Aha. Are you scared? You can't bet because you think you'll lose. You can't even last for one gak, yet you say, 'Ooh, I can't sweep if sumone's awound' in a nasal voice."

At that, a vein popped on Seol Ri-ri's forehead.

"Fine."

And then, she laid down on the bed.

The bed was tiny to begin with, as it was in a shabby countryside inn that barely had the basics.

Qing shifted her body within the covers, leaning on Seol Ri-ri's torso and placing her arms and legs on her as well.

"Move. Uncomfortable."

"Isn't that even better for Young Lady Seol, then? If someone's there and it's uncomfortable, you're less likely to fall asleep."

"Even if I don't do this-"

"Aha. This is for fairness. I'm trying to make sure you don't try to stay awake by tensing your body, pinching yourself, or holding your breath. Now then. One gak. Start."

Lying in warm blankets and hugging the cool, human-sized pillow, whether due to the aftereffects of the Ice Arts or her constitution, was so comfortable and cozy that it felt like paradise.

And after a while.

"……Snore."

Qing, slowly falling asleep, could hear the sound of snoring in her ears. Due to her cold, it was a cute, rhythmic snore that went snore, huff, snooore.

After all, she had a cold, had taken medicine and collapsed, then woke up and drove a carriage while being constantly rained on.

No matter how sensitive she was and how she claimed she couldn't sleep with someone around, how could she possibly endure for one gak with all that fatigue?

And for some reason, though she hadn't used much strength, she felt like she had exerted herself more than she thought. She was more exhausted than she should be from just running around in the rain.

At any rate, Qing was also quite tired, so as she listened to that adorable snoring, she couldn't help but feel drowsy……

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Having slept soundly from early evening, she woke up not knowing what time it was.

Originally, she could roughly tell whether it was morning, forenoon, or afternoon by the sunlight entering the room, but the room was pitch dark, and all she could hear was the sound of rain pouring down.

Her cold seemed to have cleared up, as Seol Ri-ri's breathing was clear without any wheezing.

Qing felt a bit disappointed.

Hmm. Her nasal voice was kind of cute, though.

Hmm. But what is left if I take away the cuteness from Young Lady Seol?

Isn't she just a pretty coachman?

Shouldn't I just tell Young Lady Seol to drive instead of hiring a coachman from now on?

After all, even if we ride together, we don't exchange a single word, so if I just put her in the coachman's seat, I can save a little money.

Hmm. Can I save money, though?

Or should it be considered spending more money?

Qing had a lot of money, but now she had even more.

Turns out, the coachman had planned to enjoy himself and then charge extra to share the good times with his friends.

He had heard that he demanded ten taels of silver.

So, fifteen bastards each carried at least ten taels of silver.

Moreover, the money pouches they carried separately were substantial.

If they disposed of the cheap weapons in the carriage's luggage compartment, they would make even more money.

Considering all that, Qing had cleared out a pile of trash from the world and earned a hefty sum of money in return.

If Seol Ri-ri had taken on the role of coachman, she would not have gained such income.

At any rate.

Hmm. It's stuffy.

In the primitive, ancient, and underdeveloped Zhongyuan, air conditioning had not been invented yet, so ah, I miss you, Great General Air Conditioner……,

Still, even though it was raining, the weather wasn't too hot, but the humidity was high. After all, even if the weather in July was cool, how cool could it possibly be?

When Qing stepped out of the room, she realized that she had woken up early in the morning.

"Ah. Master. Have you awoken?"

The innkeeper's daughter, not even a server, who had been diligently wiping the tables since morning, spoke to her.

'Master' was a form of address one would hear in the countryside.

"Yeah. Why is it raining so much?"

"It was too dry this spring, so it seems like all the rain that didn't fall then is pouring down now, as the elders said."

"I guess it was quite dry."

From the time she left the Divine Maiden Sect until the Wulin Martial Arts Tournament, there were unusually few days of rain during the early spring.

She seemed to remember hearing that the level of the Grand Canal in Kaifeng was only half full.

"Hmm. So, when will the rain stop?"

"Hehe. How would I know the will of the heavens, Master?"

"Is that so……"

In the primitive, ancient, underdeveloped Zhongyuan, weather forecasting was not yet widespread. In fact, weather forecasting was an incredibly advanced technology.

Of course, weather forecasting was very important.

Thanks to that, there were geomancers, astronomers, and weather analysts in Zhongyuan, who were basically weather forecasting amateurs.

However, their accuracy was roughly at the level of saying, 'Ah, I thought it would rain' after it had already started raining.

After all, if it rains, you just have to deal with it. There's not much else to it.

Qing then brought up the main point.

"I need to find someone to drive a carriage to Luoyang. I'll pay one tael of silver for the fare."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Originally, the journey from Dengfeng County of Mount Song to Luoyang could be done in a day by carriage.

They had some fun along the way, earning some money and delaying their journey by a day.

However, since it wasn't a trip with a set deadline, they leisurely set off from the countryside early in the morning and arrived in Luoyang around late lunchtime.

And so, Luoyang!

Luoyang was one of the three ancient capitals of Zhongyuan……

TL Note: Skipped some unnecessary historical exposition.

Anyway, it was a city she had been to once before, and since it was raining, she couldn't properly sightsee, so she wasn't particularly impressed.

Thus, they went to a stable and returned the carriage.

"Hey. Aren't you going to manage your coachmen? People know that coachmen are no different from thugs, but they shouldn't be this bad."

"I apologize, I apologize……!"

"Just an apology? This stable is done for. It's a den of rapists. I'm going to tell everyone about this."

"Oh no, please don't."

Qing skillfully extorted a small compensation.

After all, wouldn't the stable know about the coachmen's misdeeds? However, they didn't particularly interfere with such personal matters.

If the coachman succeeded in his side job, there would be no rumors anyway, and if he failed, they would just drive him out and pay a small consolation fee.

It wasn't that Qing was particularly vicious and extorting money as a bad customer, but rather that she was claiming the compensation that should be rightfully received.

"Hehe."

Qing, with a clear voice full of laughter. She seemed to be in a very good mood.

At such times, a companion with common sense and empathy would ask, 'Why are you in such a good mood? Is something good going on?'

However, Seol Ri-ri, besides being equipped with coolness as a human-sized hugging pillow, was deficient in all aspects as a travel companion.

She was a penniless beggar who couldn't even hold a conversation and had an ungrateful attitude to boot.

Honestly, even her sworn sister wasn't this useless.

Even her sworn sister would always hug her, offer her food before eating it herself, carry her things, and even lift her up when her legs hurt.

She might have been foolish, but compared to Seol Ri-ri, who was overflowing with fullness in her inner self, it was rude to even compare the two!

Goodness, how in the world is there someone less useful than Gyeon Pohui?

Why does such a trivial and useless human being even live and breathe!

Qing sighed deeply as she looked at Seol Ri-ri, who was sitting at the table.

Her silver hair, a side effect of her martial arts, gave her a mysterious appearance, but her expressionless, blank stare made one wonder what she was thinking.

Ah, that face.

If it wasn't for that face, I would have abandoned her already.

She's just a pretty face, a self-propelled, functional hug pillow.

Wait, then, is it a hug doll instead of a pillow?

Anyway, whatever. Human-sized hugging pillow.

In the end, since Seol Ri-ri failed to fulfill her role as a proper companion by asking why she was in a good mood, the reason remained eternally shrouded in mystery……

Was what the server thought when he asked instead.

"Hey, server. You know the Black Shadow Association, right? Those somewhat cocky minor villains in Luoyang?"

That's right.

A gentleman's revenge is never late, even after ten years. This was the spirit of Zhongyuan, passed down from ancient times.

The spirit of Zhongyuan was to never forget a grudge for a thousand, even ten thousand years, while disregarding any favors received.

It had only been about three years since Qing's humiliating retreat from Luoyang, making it the perfect time to settle unfinished business.

However.

"Ah. Those guys? They're ruined."

"Eh. Why? Why did they go under?"

"I heard they offended a high-ranking noble from a Wulin Clan."

The server explained for the price of twenty coins that martial artists from the Hebei Paeng Clan and the Huang Clan had raided their businesses, revealing their龌龊 [wòchuò] (sordid) crimes.

As a result, other minor villains in Luoyang immediately cut ties, claiming ignorance.

Ultimately, having received attacks from two of the Ten Great Clans, they were completely destroyed, not even leaving a foundation stone behind.

At that, the Mission Window flickered, displaying a notification that the Sudden Mission had been completed.

For some reason, it felt like she was being mocked, as if it was saying, 'Too late, you idiot'.

Wait, what? Why!

The Paeng Clan and Huang Clan are Sanie and that tiny guy!

Did these guys have fun without me!

I can also commit familicide!

I'm really good at killing bad guys!

Qing's mood plummeted.

I trusted them…….

It was the pain of being betrayed by trusted friends.

How could they do something so fun on their own without me?

If Peng Daesan and Hwangbo Uncheok had heard this, they would have been speechless, wondering what the hell was going on.

To be fair, they had mobilized their clans' martial artists to deal with the aftermath and shed blood to protect Qing.

Hwangbo Uncheok had simply been enraged by Qing's words and joined in with his usual meddling, or rather, his sense of justice.

Fortunately, Qing was able to quickly regain her composure.

Well, what can I do about it since they're already ruined?

Goodbye, my Luoyang. My grudges and enmities.

But, um. Ah. This looks delicious.

Because the food started to come out.