\chapter{Journey to Zhongnan (1)}

Her appearance was not one that could be described as stepping out confidently.

Her face was as red as a persimmon, and she stood awkwardly, clutching the hem of her clothes. Wait, was she not even wearing anything underneath? She was also at a loss for what to do, clearly embarrassed and ashamed.

Qing had left, so she hurriedly chased after her, but she seemed aware of her own appearance. Whether it was a good thing that she was aware or whether one should admire her determination, it was hard to say.

"Honestly, it's quite indecent. And why wear white of all things? Do you want to proudly announce to the entire world of Zhongyuan, 'Here are my nipples'?"

"Ugh."

In Zhongyuan, a chest covering was, strictly speaking, more of a nipple covering.

After all, it was closer to an apron that hung down to the solar plexus, tied around the neck or shoulders, with either one strap below the breasts that tied in the back or none at all, leaving it half-and-half.

Therefore, it had almost no function in shaping or stabilizing the breasts, and its main purpose was to prevent the protrusion from being noticeable by adding a thick layer of cloth around that specific area.

Of course, that wasn't all there was to it. It also served the primary purpose of improving the comfort of wearing clothes with a soft lining.

The reason for concealing the protrusions was that the ancient, primitive, and uncivilized society of Zhongyuan considered it extremely vulgar and shameful.

"Wait for me. At least give me time to cover myself with a blanket-"

"What if I don't wait for you? Are you going to follow me like that?"

At that, Seol Ri swallowed hard and then replied with a very determined expression.

"Yes."

Can't that stuffy nose of hers be unclogged somehow……?

"Hmm."

Aside from that, Qing pondered for a moment.

Honestly, waiting for her wasn't a big deal. And it wasn't as if a dramatic reunion with that Seol bastard would occur just because Seol Hwa followed her.

But somehow, it felt unfair. It seemed like she was intentionally acting this way, thinking that since Qing had bought her food and slept with her, she could use her kindness as if it were her right.

If it were someone mentally unwell like Young Lady Moyong, she could help them recover, but…

"I'm leaving. Young Lady Seol can do as she pleases."

Qing turned around and walked down the stairs.

If she didn't follow, it would mean she was definitely a stalker, intentionally acting like that because she was sure Qing wouldn't just stand by.

But if she followed… Well. That would be something in itself.

If she was willing to endure the shame of following her in that state, it would mean she was truly determined to fulfil her mission and punish the enemy of her sect.

Then, it would be impossible to let her meet with that Seol bastard.

Thus, Qing walked down the stairs, making more noise than usual.

Just then, a group of men were coming up from the lower floor, snickering among themselves, but upon seeing Qing, they suddenly adopted stern, serious expressions.

It was because men often thought they looked cool when they kept a straight face, especially when they didn't think they were particularly handsome.

After passing the men, Qing glanced back and saw a woman standing suspiciously close to the wall at the stair landing, pressing her forehead and body against it.

Fortunately, the men, after looking at her closely, passed by without looking back.

Originally, men were sad creatures who, once conscious of something, found it harder to look directly at it.

In that state, Seol Ri turned her head to confirm that the men had disappeared, then turned it the other way to meet Qing's eyes.

Tears welled up in her eyes.

While doing so, she slowly started to shuffle towards Qing sideways like a crab.

Ah. So she really did follow me in that state……

Now that I see it, she is not the Ice Flower, but an idiot.

Or maybe a moron. It might be appropriate to drop the 'flower' altogether and just call her a moron.

It almost seemed like she was intentionally acting cold and aloof to avoid revealing her true nature.

"Are you going to walk around in the market looking like that?"

"Yes."

"Haaa. Wait in your room. I'll get you some clothes to change into."

Seol Ri carefully observed Qing.

It was obvious that she was trying to discern whether Qing was lying.

"Ugh, seriously. Have I ever lied to you? And wipe that snot."

Seol Ri wiped under her nose, looked around, and then wiped it on the wall.

Then, she turned around and went back up the stairs, still maintaining her aloof and haughty expression.

Sigh. I wish she would at least reply.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing decided to just take the dimwit surnamed Seol with her.

There were two minor reasons and one major reason.

Minor reason one.

It was obvious she wouldn't let go even if Qing tried to shake her off.

It didn't seem like she would give up just because she was shaken off, considering her willingness to chase after her even in that state.

Minor reason two.

Although her actions were clumsy and frustrating, she had a certain cuteness to her. Honestly, if her face wasn't to Qing's liking, she would have tied her up and shipped her off to the Wulin Alliance via express delivery.

And the major reason was quite serious.

I wonder… Can I even travel Jianghu alone like this?

Even last night, she couldn't sleep alone.

She didn't know when it started.

But if I disappear, shouldn't at least one person see that happen so they can inform my teachers, friends, and the disciples of the Divine Maiden Sect?

If I suddenly disappear from the world, they won't even know to look for the day I vanished.

Even if that wasn't the case, there was an unfounded expectation that if she was touching someone, she wouldn't suddenly return to the modern world.

At the very least, I need someone to hold hands with while sleeping. I need someone to be close to me, to be as close as possible.

So I need someone next to me when I sleep.

So, what can I do?

Since there's someone next to me.

I should just think of it as carrying around a big doll to hug.

What do they call that……?

Ah. Right. A body pillow. A body pillow.

The body pillow seemed to be quite pleased with the clothes she bought for her.

Even without any expression, it was surprisingly easy to read her face because of the lack of expression.

A person's expression changes drastically with even slight angles of the corners of the eyes or mouth, so it was actually easier to read the body pillow, whose face was originally expressionless, by the slight curl of her lips.

Come to think of it, she was all smiles when eating. Or maybe not? Did I see wrong?

"Do you like it?"

"Yes."

But the body pillow was severely lacking as a travel companion, scoring only one out of a hundred as a conversation partner.

"Thank you."

At least she bowed her head, which was not so bad. She was a body pillow that knew shame, after all.

"Let's eat breakfast first. Young Lady Seol, is there any food you like?"

"Yes."

Qing's eyes narrowed.

"Young Lady Seol. When most people ask that, they're not just asking whether you like food. I'm asking what you like because I'm going to buy it for you."

"I know."

"You know, but all you say is yes? What's this? Are you trying to pick a fight?"

"I'm sorry for taking your money……"

Surprisingly, she's quite full of shame……

Qing noticed an unexpected side of her.

She did ask, but her breakfast choice was already decided. Jeonbyeong, or pancakes.

Of course, the way people of Zhongyuan named things was extremely bizarre, so anything thinly spread and cooked was called a jeonbyeong.

As a result, the taste and appearance varied greatly.

In terms of Qing's hometown food, a buchimgae was obviously a jeonbyeong, an egg fry was a jeonbyeong, a hamburger patty was a jeonbyeong, a pancake was a jeonbyeong, and a hotteok was also a jeonbyeong, with hotteok being one of the most famous types since it originated from Zhongyuan.

From what Qing had tasted, everything was delicious and went down easily, but the closest type to a pajeon was a dish called byeongjabeong.

Byeongjabeong was a pajeon without green onions.

People of Zhongyuan would add ingredients on top of the byeongjabeong and roll it up to eat it, but Qing didn't need other toppings and ordered a lot of green onions, a lot.

As Seol Ri looked at the mountain of byeongjabeong and the pile of sliced green onions, she casually said a word.

"I want to eat porridge."

Due to her stuffy nose, it sounded like she was acting cute.

Since her face was incredibly attractive, Qing couldn't resist her aegyo.

"Porridge? Alright, let's order some then. Waiter? What kinds of porridge do you have? Something that's readily available."

"Today, we have honeyed pine nut porridge, rice porridge, and minced meat porridge."

"Hmm. Wait a moment. Pine nut porridge? Rice porridge? Minced meat porridge? Ah. Now that I hear it, it sounds delicious. Bring two servings of minced meat porridge."

Seol Ri's ears perked up at the mention of minced meat porridge, which seemed to have caught her interest.

For reference, the porridge of Zhongyuan was characterized by being thoroughly boiled until the contents were completely dissolved, unlike the porridge of Qing's hometown.

Therefore, the rice grains were completely disintegrated, making it somewhere between porridge and gruel.

And so, with a full serving of byeongjabeong each and a large bowl of porridge in front of them, they enjoyed their breakfast"Ha-eung, hoo, hoo, hoooo, haang……"

Wow. She's really just scooping up that hot stuff and eating it, huh?

Originally, porridge was as hot as lava when it was boiling. In Qing's hometown, it was common for people to burn their tongues on piping hot porridge, causing the spoon to melt and leading to the consumption of a porridge mixed with molten metal.

However, although it fell just short of the melting point of iron, boiling porridge could easily melt a person's tongue.

And yet, she was just scooping it up from the bottom without even blowing on it and putting it in her mouth.

The sound of 'hoo hoo' was not to cool it down but because her nose was stuffed, forcing her to breathe through her mouth.

Moreover, the sound was quite lewd.

"Haeu-eung……"

Come to think of it, back in her hometown, there was a term for people who ate in such a vulgar manner. What was it? Food fuckers? Something like that.

"By the way, it's raining cats and dogs."

At that, Seol Ri, who was hesitating between soy sauce and vinegar while holding her byeongjabeong, looked at Qing once and then turned her gaze back to alternating between the two condiments.

Ugh, seriously. Shouldn't there be a response like, 'Yes, indeed. Heavens, what kind of rain is this?' or something similar?

What kind of conversation is this one-sided?

Still, it was an opportunity to remind her that she shouldn't expect a two-way conversation with a body pillow.

But it would be bad for the body pillow's nasal health to go out in the rain with just an umbrella hat.

It didn't matter to her, but more importantly, it was annoying to be out in the rain. At first, it might feel nice, but it quickly becomes damp, humid, and sticky.

She had no choice but to rent a carriage.

Renting a carriage from the stables and hiring a driver from a waiting list of job seekers, who had a gentle and honest impression, went smoothly without any sense of incongruity.

Qing could now proudly say that she was a capable wanderer, able to handle things on her own.

"The most important thing to watch out for when renting a carriage is the person. There are many coachmen who turn into robbers, thinking you're an easy target. Don't go for ones that are too cheap, but don't get ripped off either. You have to find someone who is honest and pay a reasonable price within the market rate."

"Did not ask."

"……Just wipe your snot."

Even knowing it wouldn't work, she kept trying to talk, which was due to Qing's talkative nature.

"I'm going to catch some shut-eye, so wake me up if anything happens."

"Yes."

With that, Qing leaned against her luggage, took out her underwear bundle, placed it against her cheek, and expertly settled into a sleeping position.

The sound of rain hitting the carriage ceiling. Since it was a cheap carriage, the soundproofing was also cheap, allowing the sound of rain to pour in.

And the sound of a useless companion who could only breathe with a stuffy nose, but at least was quiet.

It wasn't a bad place to doze off, even if she couldn't talk.

Thus, Qing skillfully leaned back and soon began to snore.

Seol Ri quietly observed Qing's face.

After some time had passed, with one person sleeping and the other just watching her sleep, Seol Ri suddenly felt the carriage tilt forward.

Not long after, the carriage came to a complete stop.

Then, the door burst open, and a coachman, who looked like the very image of a merciful Buddha just moments ago, pointed a sword into the carriage.

And then, he opened his mouth with a benevolent face and spoke.

"Hehe, it seems like some delightful ladies have come to offer their bodies of their own accord. This old man had such a hard time because his yang energy was practically bursting at the seams, you see?"