\chapter{Change the Course to North by Northwest (1)}

A-Qing demonstrated judgment befitting a person of the modern era.

If you run away half-heartedly, you will surely be caught.

It was a lesson taught by many modern stories.

As such, she spent ten days solely running, eating, and sleeping.

But at long last, Qing was finally able to let loose and once again immersed herself in the hobby she picked up in Wulin.

It was gourmandism.

{\itshape Ah, the fragrance of this chilled inn.

It has truly been a long time of humiliation.}

As she was sitting at the table, the server approached her.

The expression on his face was distinctly uncomfortable, though.

With the maturity of a second-year living in Wulin, she now knew the dining etiquette of Zhongyuan. 

In an inn, the seating arrangement was important.

The best seats were considered to be at the center and by the window and the value of a seat decreased the further away it got from these spots.

The worst seats were those near the back door leading to the backyard.

Those who ate cheaply should automatically go to the worst seats.

It was an unspoken rule of the inn.

However, A-Qing boldly took a seat by the window where the sunlight shone brightest.

After only running, eating, and sleeping for ten days, she looked like a complete mess.

As such, it would be odd if the server's expression was bright and welcoming when A-Qing took the best seat.

However, all these rules meant nothing in front of a sword.

The server did not dare to say anything else and only acted a bit rudely because of the sword A-Qing leaned on the table.

"What would you like?"

"Kekeke..."

A-Qing let out a bizarre laugh.

At that moment, when the server's face crumpled, A-Qing slammed a silver sycee\footnote{Ancient Chinese currency, shaped like a boat. A staple of Ancient Chine-period movies/ dramas} on the table!

"Heuk!"

"That's right. Its a silver sycee. Bring me the best and most delicious dishes you have. Three of them. And bring alcohol. The expensive kind."

"Understood!"

The server took a deep breath.

"THE GUEST HAS ORDERED A BRAISED PORK BELLY! SWEET AND SOUR FISH! STEAMED BABY FISH! AND BAMBOO LEAVED LIQUOR AS A SIDE!"

The more expensive the order, the louder it should be announced.

It was a server's duty.

{\itshape This customer has ordered expensive dishes!

Everyone in the inn, look here!

This person is ultra-rich. Ultra-rich, I say!}

Through this, it was evident that the Chinese truth of vulgar materialism had been a characteristic of the continental nation since ancient times.

But you can only know once you experience it yourself.

\textit{It feels fucking lit!}

The other customers in the inn looked at A-Qing with envy.

For example, it was like this.

{\itshape Gosh, Braised Pork Belly, Sweet and Sour Fish, and even Boiled Baby Fish!

Oi, oi, how wealthy is this guy!}

And then, the Greatest Beauty in the City (A Paragon of Virtue) should come over and hand her Bamboo Leave Liquor, but-

Tsk.

A-Qing frowned.

It was because the imagined Greatest Beauty in the City (A Paragon of Virtue) was looking down on A-Qing with a contemptuous expression.    

In Luoyang, A-Qing had her fill of pleasing sights.

And even then, not once did she receive a friendly glance.

\textit{Am I selfish for just wanting someone to smile for me?}

It was at that moment that the server appeared and carefully placed down the alcohol and dried snacks before retreating backwards.

At any rate, A-Qing was in a good enough mood to spout all such nonsense.

There were three occasions when she was elated.

Either when delicious food was in front of her.

Or when enjoying getting soaked via a serious life-and-death duel.

Or when she had a lot of money.

In that sense, the past ten days of fleeing were more than worth it.

Though she didn't know her name, the Lady from the Black Shadow Association seemed to be dearly loved by her family.

And it was because parental love sometimes manifested in the form of gold.

Moreover, she could tell how spoiled she was by her shitty behavior and Evil Karma.

\textit{This was why home discipline was important, you know?}

The gold from more than two coffins were enough as a lesson fee for the Black Shadow Association Leader.

{\itshape That's what you get for letting your child grow up crooked. She croaked because she didn't know her place. Fuck around and find out. And she found out.

I hope you raise your other children better.

At this rate, can't I be considered a great teacher on the level of Teacher Oh\footnote{a Korean TV shows personality}, the childcare expert?

Also, honestly, theres no evidence that I killed her, ye?

Once I came to my senses, she was already dead, you know?

Its possible she wrapped her hair around my hand and then committed suicide by cutting off her head. Right? I think thats possible.

So, there's not a single thing I did wrong.

Rather, I've cleaned up three dirty pieces of shit from the world, so...

Fuck, the food is taking fucking forever.}

A-Qing cursed.

As to why, it was because she had a glass of alcohol.

\textit{Kuahhh, this is fucking bomb.}

The love that the people of Zhongyuan held for strong liquor was truly out of this world.

The Bamboo Leave Liquor, contained in a cup barely big enough for a spoonful, scraped harshly against her tongue and throat before blazing up to the solar plexus.

\textit{Is alcohol bitter for you? Well, pussy, for me, its sweet.}

After all, Bamboo Leaved Liquor was originally supposed to be sweet.

\textit{But what the hell? Is this supposed to be this spicy? Why is the alcohol spicy?}

A-Qing tilted her head.

The spicy aftertaste that sharply arose was peculiar, yet it was also exquisite.

\textit{Meh, whatever. I guess its supposed to be like this.}

As she kept slurping up the liquor, the dishes arrived.

Pork with a golden-brown exterior.

Soft on the inside and soft on the outside as well.

It was served with some sort of sashimi with fried eggplant and vegetables on the side.

There was something murky in the center, but she wasnt too sure what it was.

It was regrettable that there was no soy sauce to dip, but the rich sweetness was excellent.

An incredibly large steamed whole fish.

The tender flesh of freshwater fish made eating it steamed a bit frustrating.

But still, it was delicious.

\textit{Overall review. Excellent. Stamp of approval.}

A-Qing nodded after having a slight taste of everything.

Now, it was time to eat in earnest.

{\itshape This pork, the taste is phenomenal!

It's so easy to pick up with chopsticks and it melts in my mouth like shaved ice. Also, the fat and meat melts simultaneously, the very definition of a rich fatty delight...}

Something murky, with a pudding-like appearance, a faint pink color, and fine veins, were visible.

Upon putting it in her mouth...

{\itshape Holy shit, it was a rich fatty taste again. But, hmm...the flavors do overlap a bit.

At times like this, I should have some vegetables to cleanse the palate 

Fried eggplant. It was fried eggplant. Delicious.

The taste is remarkably stable. But-}

"Hey, kid?"

A-Qing cocked her head.

She hadn't been able to wholly enjoy the food because of the kid who had been maintaining a subtle distance and watching her eat.

Was she perhaps around ten years old?

The child was small and skinny, pitifully so.

{\itshape When it comes to eating, even dogs shouldn't be bothered. And looking is a form of violence! Violence, I tell you! Did you think I'd be swayed by your little innocent eyes? If you keep looking at me so pitifully, do you think I'll say, 'Hey kid, try this', or something?

Ha. How ridiculous. If you really thought I would do that, then you are completely right. I'm a softie.}

"...?"

Being hungry to the point of sorrow was genuinely sorrowful. Seriously.

A-Qing had learned this painful truth through her life in Jianghu.

Especially when someone was gobbling down dishes next to her while she was chewing on mere dumplings. The urge to slash them with a knife was something she had to do her utmost to resist. 

After all, in Zhongyuan, dumplings were nothing but bread without any filling.

A-Qing was currently quite wealthy.

Honestly, she could be considered even more wealthy than she was purely because she never once thought about her future wealth. After all, she was more than capable of spending whenever and however she wanted.

And that was reason enough to cause this unnecessary kindness.

"Want some meat?"

"!!!"

The childs eyes widened into saucers.

Finding that adorable, A-Qing picked up a big piece of meat with her chopsticks and offered it.

The child looked at the meat with trembling eyes, then hurriedly looked around, and then looked at the meat again.

And finally bit down.

Though the child didn't speak, her expression did.

It was as if she was wondering how something this delicious could exist in the world, thus feeling betrayed by how she had lived all her life without knowing this.

A single tear rolled down the childs cheek.

A-Qing giggled as she just handed over the chopsticks for her to eat.

"Okay, well then. Sit here, yes, yes, Kid. You know how to use chopsticks, right? Help yourself, okay? I'm a cold person who doesn't go easy on someone just because they're a child. After all, one must know how to fend for themselves. And of course, that includes eating."

A-Qing started to eat ferociously.

The child hesitated at first, but seeing the dishes quickly disappearing, she bravely reached out with the chopsticks.

From then on, there were basically two beggars at the table.

It was during this time when it happened.

"Ming!"

With a scream-like shout, a woman came rushing in.

A-Qing could have easily stopped her since she was a Master, but she let her be because of her desperate expression and complete focus on the child.

The woman embraced the child as if snatching her away.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"T-Thank you! Great and Honorable Expert!"

A middle-aged woman, about the age of a mother, kept bowing her head.

Her name was Yang Xiaoyue (楊小越) \footnote{Yang Sowol/ 양소월 in the original text}.

The gratitude was so overwhelming that it was actually somewhat burdensome.

"It's just because the kid was cute, thats all. Changming? Haoo olb iz our Cuhngmeeng?"

Instead of answering, the child blushed and averted her gaze.

\textit{Aw, look at this little kid being all cute.}

It was right when A-Qing was smiling warmly.

"Um, Great Expert.."

"Yes?"

"Changming has turned sixteen this year."

"What?"

A-Qing looked at the childs thin appearance.

No matter what angle she looked at her at, the child did not seem to be over ten years old.

The child is a bit frail, so she hasn't grown as much as other children her age.

\textit{Mother, it seems to be more than just a bit...}

A-Qing held her tongue.

Now that she knew his age, the child's flushed face seemed to mean something different.

It wasn't bashfulness, but shame!

If she was sixteen, so like.

It had been so long since she attended school that she couldn't immediately match the school year with age.

\textit{1st grade in elementary school is at 8 years old? Is that right? So then, 9, 10, 11, 12, 13, 14, 15, 16.}

A-Qing folded her fingers one by one and barely finished counting.

\textit{She's a 3rd grader in middle school? This little kid?}

Since she made such a comment in front of a middle school 3rd grader, it was only natural for the child to feel ashamed.

A-Qing was astonished.

And so, she alternated her gaze between Yang Xiaoyue and Chen Changming (陳江命)\footnote{Jin Jangmyeong/ 장명 in the original text}.

Yang Sowol was a beautifully aged madam.

Even though her attire was simple, there was a certain dignity about her.

Changming was a little kid with hollow cheeks.

The child looks like she hasn't eaten, but the mom looked completely fine?

Could it be...Perhaps?

Moreover, the child couldn't even speak.

Yet still, she had let her guard down because she seemed like a decent lady due to her Righteous Karma.

A-Qings gaze sharpened.    

"Uh, Great Expert, this is a misunderstanding."

"Misunderstanding? What misunderstanding?

"The child is a bit, no, very sick, so..."

Yang Xiaoyue's expression was filled with sorrow and apology for her daughter.

It was undeniable evidence of her deep maternal love.

\textit{Ah, it was a misunderstanding, after all.}

A-Qing felt awkward and embarrassed.

"Did you perhaps also take the wrong herbal medicine or something?"

"What're you talking about? Ugly."

A-Qing was startled.

She spoke!

{\itshape What the heck! She can speak, after all!

No, wait, but at sixteen, of course she would be able to speak. 

Rather than that? Did I hear something wrong? The content? A bit?

Ehhhh? After all I fed her, what the fuck is up with her attitude?}