\chapter{Change the Course to North by Northwest (6)}

In a distant past, a Daoist Monk with the surname Zhang established a Daoist temple at Purple Cloud Peak of Mount Taihe.

One day, Zhang dreamed of meeting an Immortal and asked for his teachings of the sword.

Upon waking from his dream and undergoing zen meditation for ten months, he found that the sword could move by itself.

Zhang then built a temple for Zen study and named it Wudang, attaching a signboard to it. 

Thus, people began to call Mount Taihe by another name.

Because it was the main mountain of the Wudang Sect, it was called Mount Wudang.

And here, there were people heading towards the Wudang Sect.

"Teacher, do you need to continue being carried?"

"Fine. This much is enough."

Then..

"Ahhhh, what a sorrow it is to be old. The only disciple I have thinks of nothing but throwing me aside every morning and evening. Ahhhh, O Primeval Lord of Heaven."

"Teacher, what is that supposed to mean? Teacher will surely live a life of eternal youth. Please know that, at the very least, your disciple always wishes for that."

"But what glory is there in living a long life alone? I, too, always pray for my disciples path to immortality."

The Daoists Monks following beside laughed.

After all, it was said that one lived longer the more they were cursed at.

"But Teacher, why are you hanging onto me like this?"

"Since it is too difficult for you to carry me, I decided to hang on instead."

"The Lord Above truly is indifferent. To leave such a living example of righteousness, an embodiment of active goodness, on this earth without thinking of calling him back to his embrace."

"If it seems like it is time to ascend and join the world of Daoist Immortals, would there be any particular reason to prepare?"

"I have found a reason. Since the Dao of the Immortals does not accept worldly connections, shouldnt the order be first-come, first-served? "

"Hoho, that is my wish. So please, try to do as such."

Huanlu (桓陸)\footnote{환육/ Hwanyuk in the original text}, the young man carrying the old man, gritted his teeth and lamented.

"My fate is indeed one of ill luck! At Mount Hua, Daoist Monk Changbin served his teacher so well that he eats elixirs like its his daily meal and is even aiming for the Transcendent Realm. Meanwhile, some haven't even seen the leftovers of Purple Night Pills. It is said that connections are the fortune of three lifetimes, so how did I end up with such misfortune!"

"Indeed, indeed, you spoke well. If my disciple were Changbin, I could truly feed him elixirs like it was an ordinary meal. It is really, truly a pity."

"Teacher! Isn't that a bit much?"

Hwanyuk was scratched.

As the attack was so softly dealt with Wudang's Tai Chi, it was clear that Hwanyuk was still a novice compared to his teacher.

They were Daoists of the Wudang Sect returning to Wudang.

The grand celebration of the Mount Heng Sects Grand Elder was a month ago and they took the rare opportunity to cultivate their Dao by enjoying the scenery of Dongting Lake.

The teacher, Dao Master Shengshou (勝手)\footnote{ 승수/ Seungsu in the original text}, consoled his sulky disciple.

"You brat, are you upset? Even if I can't take care of my disciple as well as Junghoo does, I have given you something far more precious, have I not? "

"From Teacher? As an unworthy disciple, I do not remember receiving anything, so what is this precious article you have given me?"

"You brat, what do you think being well-endowed means? Whether it is reaching the Transcendent Realm or whatever, he is beneath you, so what is the point in being jealous?"

"Come to think of it, Teacher's words are indeed like precious jade. Isn't it hard for Teacher to cling to disciple? May this unworthy disciple dare to hold onto Teacher's buttocks, that is no different from the sk- Mm?"

Huanlu's expression became serious.

"Did you hear that?"

The sound of a human scream.

It was a scream that was faint yet so desperate that just hearing it was enough to send shivers down his spine.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A man with a face akin to a rat was crawling on the ground in a miserable state.

When he looked up because a shadow was suddenly cast, A-Qing was squatting and looking down at him.

"P-Please, save-"

"Me? How? Do I look like a doctor to you?"

"Please save me, I beg you, please-"

"That's not my area of expertise, soooo..."

Suddenly, a scene came to mind.

Friends were gathered in front of a flower bed.

Someone was yelling to come quickly.

A worm was crawling on the cement floor.

And there was a magnifying glass in a friends hand.

It was the day when they were collecting sunlight, pushing each other aside and saying it was their turn because they wanted to try too.

That day, there was a friend whose name and face she didn't really remember.

But the desperate wriggling, the worm's body quickly swelling and puffing up under the small glass lens the size of a child's palm, was vivid.

It was a memory from some part of her childhood.

"Huh, right."

"Sav-"

"Didn't the worm wriggle more than this?"

"Please save me, please-"

"But doesn't it hurt? Wouldn't it be easier to just die? Why not just ask to be killed?"

A-Qing tilted her head, seemingly unable to understand.

The rat-faced man looked up at A-Qing.

And then, their eyes met.

In the shaded eyes of A-Qing, who turned her back to the sun, a tumultuous gleam flickered.

At first glance, it was purple, but upon closer inspection, it was also red like blood and blue like thread veins, as well as had the yellow blaze of the sun.

It was entirely black and sometimes white, yet also transparent.

It was truly a color that did not exist anywhere in the world.

When the Killing Star of Heavenly Slaughter seeped into the marrow, it illuminated the world with an seditious starlight.

"Demon! It is a monster!"

As she suddenly raised her head, a young man with a sword charged straight at her.

A-Qing swung her sword in response, but the young man stepped into the air, leaping and dodging.

There was an unspoken rule in the Wulin of Jianghu. 

After witnessing the marvelous footwork of a direct disciple of the Wudang Sect, one must express admiration and respect.

Any cultured martial artist would have to exclaim, 'Indeed, it is Cloud-Ascending Ladder!'.

However, A-Qing lacked such refinement.

Instead, she was overwhelmed by the unexpected aerial maneuver and struggled to defend against the onslaught.

The young man changed direction seven times in mid-air.

He moved right, left, up, and in all directions, before finally kicking off an unseen point in the air and charging instantly.

The tip of the sword pressed forward like a massive mountain.

A-Qing gritted her teeth and swung her sword horizontally.

The Moonlight Sword, narrowly avoiding the young man's sword tip, twisted its trajectory desperately.

The swordplay that had charged right before her eyes slipped away to the right.

But then, she saw the young man's empty left hand.

A fist that clenched one digit at a time starting from the pinky, rotating.

 \textit{ Oh shit. Oops.}

A-Qing poured Inner Qi into her heels. 

Thump. A-Qing flew through the air and tumbled to the ground.

Standing up amidst the churning nausea, she vomited a bowlful of black blood.

Unfortunately, A-Qings front was more protruding than others. As such, the vomited blood completely soaked her clothes, leaving them damp.

"Mm...?"

A-Qing blinked her eyes.

Why did I feel so refreshed even though I'm being hit?

In truth, both the Seven Stars Qi and the Demon-Subduing Fist Technique of Wudang were originally endowed with excellent exorcism and purification properties.

The combined effect of two strong Purification Qi hit A-Qing with more than triple the purification power.

Fortunately, A-Qing was the holder of the Yue Maiden Cultivation Technique.

This technique was also a martial art of Daoism.

It was difficult for Internal Qi Cultivation's of Daoism to affect each other significantly.

Daoist Qinggong tended to slip past each other without much harm, as if to shout 'It's not like we are strangers!'. 

However, the Yue Maiden Cultivation Technique, which faced the Killing Star of Heavenly Slaughter alone, exerted some effort in resistance upon receiving the fresh and clear Qi of Wudang.

The Killing Star of Heavenly Slaughter from the marrow seeped out with the blood and the tainted blood exited the body.

It was a stroke of luck.

Though at best, it just postponed the inevitably flowing time of the destiny that would one day touch upon Heavenly Slaughter. 

For some strange reason, she felt refreshed.

A-Qing returned to her usual self and shouted.

"To think you would be so cowardly to ambush me from the front!"

"...What?"

"There is no need for words! Today, at this place! No disgusting, heinous, and perverted fuckers will survive! Die, pedophile!"

This was the Art of Bullshit that A-Qing would only display when she gained unwarranted confidence.

After all, the hit she received wasn't all that bad.

She was only slightly startled by the novel three-dimensional maneuver, but if she just pressed him down so he couldn't jump, that would be the end of it.

Cloud-Ascending Ladder might be a marvel of Wulin, but the lore of the Yue Maiden Footwork was a forgotten legend, as well as a myth.

A gravity-defying footwork superior to any type of three-dimensional maneuvering.

As the suddenly floating figure rushed towards him in the blink of an eye, Hwanyuk panicked and clashed his sword against her.

"You fucking pervert! Child molester! Horny son of a bitch!"

The phrases and trajectories the sword drew were certainly threatening, as it was hard to discern what was true and what was false. However, the continuous stream of curses that were being stuffed into his ear was even more horrifying.

"She's a child who hasn't even grown up! And yet, your dick still stands at attention?! Fuck, aren't you the least bit ashamed?! Do you not pity her?! Even beasts don't fuck with their young! You're worse than even beasts! No, I feel sorry to the beasts for even comparing them with you! Cut off your dick! Rip off your cock! Do it!

"W-Wait, wait a minute!"

It was then.

"Halt!"

Hearing the urgent voice and the sound of rushing footsteps, A-Qing quickly created some distance.

{\itshape  Tsk, why are there so many fucking pieces of shit trying to do something with that young kid? Wulin is going really well.

Might as well finish with the Buddha's Palm and run away.}

That was what A-Qing thought as she eyed the young man

Until she suddenly noticed the count of his Righteous Karma, 57.

\textit{...What? Why is it high?}

Then, martial artists wearing indigo uniforms of the Wudang Sect surged forward. Despite their various numbers, they were all people who had achieved Righteous Karma. 

Among them was someone who had set a new record. 183.

The old man with 183 spoke.

"First, calm your rage, Fairy. There seems to be some misunderstanding here."

"Misunderstanding? So it's okay to hit people if it's a misunderstanding? Can't you see this?"

A-Qing flapped the chest area of her blood-soaked robes, drawing attention to it.

Everyones gaze wandered around, clearing their throats and looking at interesting events unfolding in the distant mountains as if nothing was happening here.

"Disciple, what exactly is going on here? Why is this Fairy cursing you like that? "

"That, uh, well, its because I definitely saw the Killing Star of a demonic human."

Dao Master Shengshou looked into A-Qing's eyes.

The True Qi of the Yue Maiden, which had completely suppressed the Killing Star of Heavenly Slaughter, was finally doing its job.

Its Qi currently emanating from A-Qing's eyes.

It was sharp and chilly for a Daoist, but undeniably of the same path.

After all, the Inner Qi of Daoists and Buddhists were usually shown in the eyes.

"Hoho, you have truly taken leave of your senses. Yet, I never expected it to be this severe. No matter how I look at it, this Fairy seems to be a fellow follower of the Dao."

"No, that woman was definitely casting an ominous starlight and trying to kill this man."

Everyones gaze then turned towards the rat-faced man.

He was in a dreadful state, barely staying alive.

Their gazes shifted back to A-Qing.

As such, she protested.

"That piece of shit is a bad guy! He's a perverted fucker who was trying to screw, no, pounce on a young kid!"

Their gazes returned to the rat-faced man.

"No, no, its not that...It was just a kidnapping."

"Heh? Look at this fucker? What? Kidnapping? Just kidnapping? You knew what would happen to that kid, right? Hah?"

"That..."

The rat-faced man could not continue his words.

A-Qing spoke up triumphantly.

"See? He's someone who was going to offer the child to a pedophile."

Dao Master Shengshou stroked his beard and spoke.

"Hoho, have I ever seen such a beast-like piece of shit in the world?"