\chapter{Change the Course to North by Northwest (4)}

\textit{Fuck, I actually almost died.}

There were several truly dizzying moments. 

Thanks to Yang Xiaoyue's help and the fact that attacks hardly came from the side where Chen Changming was, she barely survived.

But Chen Changming wasnt attacked at all.

It meant that the target of all those villains gathered in the inn was to abduct this bratty kid.

And to think she was almost stolen away like some spoils of war that would be made as a concubine.

What's with her? Is she some kind of princess?

But she doesn't quite look the part to be called a princess.

At that moment, Yang Xiaoyue gave a deep bow to A-Qing.

A-Qing was startled.

It was quite burdensome, no, beyond burdensome, seeing as she was old enough to be her mother.

"Once again, I am in your debt, Great Expert."

"Huh, debt? No, no, no. Its nothing. Its rea-Ugh."

When A-Qing waved her arms in protest, she choked back a scream.

Blood was dripping from her arm.

\textit{Its okay when its someone elses blood, but when its mine, every bit feels precious. Is that selfish of me?}

"Great Expert, your wound!"

"It's okay. I just need to spit on it a bit."

A-Qing didn't need to worry about any infections.

All she needed to do was apply some medicine and rest. Then, it would heal.

Though it would take some time and be quite inconvenient.

"But Great Expert, your arm!"

"Ah shit, once again, my patience is..."

"Great Expert?"

"It's okay. Losing an arm is nothing. Its fortunate that the child is safe. Oh well."

\textit{I did it!} A-Qing smiled like a fool.

Rather than that, I need to treat it quickly.

Fortunately, Yang Xiaoyue knew some simple medical techniques.

She even had some decent medicine for weapon wounds.

But sadly, there were also unfortunate aspects.

There was no way to anesthetize the pain.

In the end, instead of anesthesia, she bit down on a handkerchief.

Thus, while pulling out the dagger and sewing up the wound, A-Qing had a taste of what hell on earth truly was.

Deep wounds turned inside out and protruded.

They were pressed down gently and sewn up with large stitches, repeating the process depending on the depth.

Afterwards, it was sewn up with smaller stitches.

By the time the wound was wrapped with a clean cloth, A-Qings eyes had turned blood-red.

It was because all the capillaries there had burst.

Of course, bursting into tears played a part too.

{\itshape Fuck Top G and all that. It hurt way too much to act all manly.

  Seriously.}

A-Qing, who was a bit embarrassed after calming down, changed the subject.

"So, what were up with those bastards?"

"That's..."

Yang Xiaoyue hesitated, trailing off.

Then, after a moment, her expression became determined.

"It would only be right and respectful to tell our benefactor."

"Huh, I wasn't that curious, though."

It was a bit burdensome; after all, she had just asked without putting much thought into it.

She was seriously not interested, but Yang Xiaoyue didn't seem to believe her. 

"Thank you for your consideration. The truth is, this child..."

She's hyping up the situation! Seems like theres a pretty big secret! 

A-Qing swallowed hard in anticipation.

"...was born with Pure Yin Blood."

What a shocking conclusion!

\textit{Pure Yin Blood! I have no idea what that is!}

Yang Xiaoyue, with her seasoned intuition and observations, realized this fact.

"Great Expert, Pure Yin Blood means...

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Yang Xiaoyue was originally a martial artist, but retired after marrying her husband and settled in a remote part of Fujian.

Her husband was a kind person, and so on and so forth.

To put it simply, it was about how happy she was with her husband.

The peak of their happiness was when they discovered they were expecting a child.

The child was frail.

Her limbs were always cold, she easily got sick, and once she fell asleep, she had trouble waking up.

Of course, that didn't mean it hindered their happiness.

Then, as the child grew and started learning basic self-defense, they realized her Constitution was unusual. 

She had some sort of meridian blockage. 

Children born with blocked meridians rarely lived past the age of thirty. 

The shocked couple sought out skilled doctors from all over to treat this meridian blockage.

The results of their findings were the worst it could be.

Innate True Qi.

It referred to the basic Qi that people possessed.

The amount of Innate True Qi varied slightly from person to person.

But, in the end, they were all fairly similar.

Though there might be tiny differences, they were not significant.

The property of this Qi also varied slightly among individuals.

They were commonly referred to as Yin, Yang, and the Five Elements.

However, even that was all fairly similar.

Once again, though there might be tiny differences, they were not significant.

But in very rare cases, a child was born with these properties at an extreme level.

Yin and Yang each had two properties.

Yin Energy was cold and dark.

Out of them, only the cold energy was separated and called Pure Yin.

Meanwhile, the dark energy was called Unorthodox Yin.

Yang Energy was bright and hot.

Similarly, brightness was called Orthodox Yang and the heat was called Pure Yang.

There were six extreme types of children born very rarely.

Boys born with Pure Yang, Extreme Yang, or Orthodox Yang.

Girls born with Unorthodox Yin, Extreme Yin, or Pure Yin.

Out of them, girls born with Pure Yin Blood were the most precious.

And this child had that very Pure Yin Blood.

Meanwhile, among Jianghus nefarious methods was something called Collect Yin Supplement Yang.

The practice of extracting Yin Energy through sexual intercourse with a woman.

It was different from Daoist Dual Cultivation.

Dual Cultivation involved both partners exchanging and circulating each other's energy, benefiting both.

That was also why it was not considered evil. And it was a Daoist practice, after all.

And among the six types of Yin and Yang Energies, Pure Yin was particularly convenient.

When combined with Yang Energy, it underlied and enhanced its warmth and brightness.

For martial artists who mastered Yang-based martial arts, there was no better elixir.

For those who had mastered Yin-based martial arts?

It was an elixir that made their Yin Energy even purer and more refined.

On top of that, what did martial artists think of elixirs?

An elixir was worth risking ones life for.

If one wouldn't risk their life for an elixir, then what was the point of preserving life in the first place? Where else would you use it?

Martial artists would literally risk death for an elixir.

As such, once it became known that a child was born with Pure Yin Blood, she would not be able to survive.

She would face the most miserable death amidst cruel suffering.

A background capable of protecting such a child from these unspeakably dire threats was necessary.

At the very least, until the child reached the realm of a First-Rate, where her Innate True Qi could no longer be taken by any means.

Fortunately, there was such a sect in the Wulin of this Jianghu.

The Divine Maiden Sect of Mount Wu.

However, the journey from the remote countryside of Fujian Province to Mount Wu in Hubei Province was too harsh for the child.

The idea of crossing half the continent with a child who was already so frail was daunting.

But after her husband died, Yang Xiaoyue had no more time to hesitate.

Thus, the mother and daughter set out together, hand in hand.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Wait a minute. So youre telling me, right now these crazy motherfuckers were..."

It meant all those fuckers were gathered here and causing this shitfest just because they wanted to shag a single middle school girl?

This dogshit was supposed to be righteous martial arts?

Aside from that, the kid's identity was somewhat shocking.

You were Female Middle Schooler-chan!?

A-Qing looked down at the kid who was snuggled onto her thigh and sleeping soundly.

She had shamelessly claimed the thighs of a victim of pain. Someone who was unable to withstand the torture disguised as treatment and could only let out streams of tears because her sobs were blocked by a towel in her mouth. 

The audacity. She was truly an evil little cretin.

"I apologize for bringing this up, but if you pity the child, would you consider accompanying us to Mount Wu?"

"Of course I would! Those horny sons of bitches will..."

A-Qing's words were cut off due to the sudden Mission Window that popped up.

\begin{quote}
[Omen, (Unknown)th Crisis]

Description: [You stand before a once-in-a-lifetime opportunity.]

Actions for Mission Completion

Righteous Karma) Take the child to the Divine Maiden Sect

Or take the child to an appropriate sect

Righteous Karma) Transfer the elixir to the rightful owner

Evil Karma) Sell the elixir

Evil Karma) Take the elixir for yourself

Heavenly Slaughtering Star) Destroy the elixir and take the lifeblood

[This choice could influence everything below Heaven.]
\end{quote}

It was a Mission Window format she had never seen before.

A Mission Window usually encompassed killing bad guys on the spot or doing bad deeds with them. That was the extent of it.

To go a bit further, it would be to kill the bad guy's friends as well.

Or kill indiscriminately, whether they were good or bad.

It had always been roughly along those lines.

\textit{If I knew this would happen, I would have read up a bit on Mission Guides.}

Character Making and Early-Game Farming Route.

The only information A-Qing had before entering the game was these two.

There was no time to look up other information.

The game wasn't that large in storage size to begin with.

After all, it installed in an instant, so she immediately started the game.

What's Omen? And what's the n-th Criss?

The condition for achieving the second Righteous Karma was the same.

But transfer the elixir to the rightful owner?

Moreover, the choice of words was unpleasantly blunt.

There was only one mission method that treated Chen Changming as a human being.

Elixir?

\textit{The fuck is up with referring to a perfectly alive child as an elixir?}

\textit{Crack}. A-Qing gritted her teeth.

{\itshape What the hell?

What am I supposed to do? What are you expecting me to do? What am I?

Am I inside a game? Am I the protagonist? What is this world?

What about the child? The mother? Are they humans or just programmed beings?

Why me? Why only me? Why? Why?

WhatthefuckisOmensupposedtobe.

WhydidFemaleMiddleSchoolerchanandImeet

Ifitsnotacoincidencebutpredestined

IfmychoiceorignoranceleadsmealongapredeterminedpathtowardsafixedendingthenafterthendI}

Suddenly, something cold touched her wrist.

With faded, empty eyes, A-Qing moved her neck like a rusty machine.

A small hand grabbing her wrist.

A hand so cold that it snapped her awake.

"It's cold..."

The child pulled on her wrist with her feeble strength.

Following her pull, A-Qings hand touched her unusually chilly cheek.

"Haaa."

A-Qing let out a deep sigh.

She felt like utter shit.

Just looking at the Status Window was enough to provoke a seizure. Wasn't that technically a disease?

{\itshape  Then is this a mental illness? Am I crazy?!

  This is quite a shocking revelation.

  You guys would know if you went through it.}

A-Qing forcefully swallowed the rising nausea.

The bitter gastric juice that momentarily reached the back of her throat didn't come out but went back down.

She harshly scratched her throat in frustration.

"Great Expert?"

"Ah. Yes. What were we talking about? Ah, right. Of course, we must go together. I can tell you this. Sure. Of course."

A-Qing responded in that manner.

{\itshape  Is there something like a Settings Window?

  So that I can turn off the suddenly appearing Mission Windows.

  This fucking piece of shit thing.}

A-Qing, instead of swearing out loud, looked down at the child's face.

The sleeping child naturally brought peace to her mind and body.

{\itshape  Perhaps humans evolved that way.

  Like to protect vulnerable children? Maybe?}

Mission or whatever, A-Qing had only one choice. 

Female Middle Schooler-chan was just a baby. Protect the baby.

That was common sense for any civilized modern Korean.