\chapter{Change the Course to North by Northwest (10)}

"Did you find them?"

"I was not able to find them."

"Why?"

"Because of the rain, the traces-"

"I am aware of that as well. But why?"

"The bitch has a brutal, cruel touch. There are more than twenty of our members void of their heads. "

"I saw that as well. But why?"

"Bodies were found in areas where no signal was sent, indicating they were discovered and killed before they could even blow the whis-"

"I am able to deduce that as well. I'm asking, why couldn't you find them?"

"..."

The Black Assassin stared resentfully at the blameless stones on the ground.

The prospective Heavenly Assassin, more precisely, the son of the Heavenly Assassin, patted the Black Assassins cheek.

"Hey. Do it properly. Theres five-hundred gwans of gold at stake."

"..."

"If we fail a mission worth five-hundred gwans, how am I supposed to face our Leader? What should I say? 'Ah, Leader, I spread the Net of Heaven and Earth, but the target suddenly disappeared. So we failed.' Should I say that?"

The son of the Heavenly Assassin kept patting the Black Assassins cheek.

"No, that won't do. I should go and say, 'Leader, these little fuckers totally messed up and couldn't even do a single fucking task. They couldn't send a signal or even hide. The Black Death wasn't like this before, but ever since the leader changed, it's become complete trash. They lost five-hundred gwans of gold just because they couldn't catch a single girl and our members are dying like flies.'"

\textit{Leader, how in the world did you raise your son?}

The Black Assassin swallowed his lament.

\textit{If your only son, barely obtained in your fifties, was so precious, you should have made him a better person before anything else.}

However, he remembered the earnest plea of the Heavenly Assassin, the godfather who had taken him in.

'The kid is like this, but he has a good heart. He's just lost without his mother for a while. Please do me this favor. As long as this task is accomplished, all talk about successors will die down. I am sincerely asking you.'

The Black Assassin swallowed his frustration.

For the sake of his godfather that he loved.

\textit{If this damn little brat became the successor, then it was time to leave this business for good.}

"...I will give it my all."

"Good. Go yourself, Black Assassin. Do not just sit around here, twiddling your thumbs. What use do you have from sitting on your ass just because you aged a bit?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Traps. Ambushes. Signals.

The more they moved, the more they saw a loss.

Then, shouldn't they just not move?    

A-Qing dug a cave that was about as deep as her height inside the pit.

Her hand wrapped in Inner Qi tore the dirt wall like clay.

Suddenly, she recalled a memory.

{\itshape Wow. If I had martial arts during trench construction, I could have been the  best ace in the military, even beyond the battalion, what is a battalion? Division...

Or maybe not? Whats the use of a single persons hands when there are excavators?

Still, if I had a shovel and wrapped it with Shovel Qi, I could have dug through soil, rocks, and tree roots without breaking a sweat.}

With such thoughts, she dug a small den. 

The dirt was pushed and roughly pulled up at the entrance.

She didn't completely block it, thinking there should at least be a hole to let air in.

The problem was Chen Changming's condition.

Her already cold body was shivering even more.

Even in the pitch-dark tunnel, she could imagine her lips turning blue.

A-Qing hugged Chen Changming tightly.

In all honesty, A-Qing was cold too.

Her stamina was drained, and as she held the cold child with her battered, wet body, it felt like she might actually die from how frigid it was. 

\textit{But if I feel cold, wouldn't it, in fact, feel hot to the kid?}

Fortunately, Chen Changming's shivers gradually stopped.

Chen Changming fell asleep, unable to overcome her exhaustion.

Her breathing was slightly rough.

Did the kid have pneumothorax or something?    

A-Qings consciousness was turning hazy.

As the nerves and tension eased, all kinds of pain rushed in.

But no matter how she went about it, it felt like a good thing.

She couldn't tell whether she was awake or not; in fact, it didn't matter since it was dark whether she opened her eyes or closed them.

When she occasionally came to, she wondered if she had even dozed off in the first place.

Then, suddenly, a whisper brushed her ear.

"...Why are you going this far?"

"What is it?"

"You could have just left me and gone."

"I didn't know it would come to this."

"Didn't know what?"

"I thought if I grabbed you and made a run for it, they would just chase after me. I didn't expect them to lay traps everywhere and act so cowardly, you know? Fucking bastards, I won't ever forgive them. Once I get out, I'll-"

"If you knew?"

"Yes?"

"What if you had known it would come to this?"

"If I had known, I probably would've just left you, yeah? So you don't need to feel sorry or anything. It's my stupidity that got me here."

"..."

There was no response.

Then, another question flew back.

"Couldn't you just hand me over now?"

"After coming this far?"

A-Qing snorted.

"'I might have killed some of your people, but it was all just to live, so I hope we can just let bygones be bygones'. I wish it's that easy."

"But-"

"You're a hostage now. If things go south, I'll threaten them with a blade to your neck and, ah, my Moonlight Sword. It was so expensive. Anyway, I heard there's a river around here, you know? I'll demand a boat in exchange for you and then run away."

After a long while, the child spoke again.

"The Yangtze."

"Huh?"

"It's the Yangtze \footnote{長江/ Chang Jiang; lit. 'long river'. Yangtze is the romanization based on French style. The 'Chang' character is used in Changming's name}. Because it's apparently the longest river in the world."

Chen Changming belatedly added that her mom told her. 

"That's funny. What a joke. The longest river is the Nile River, you know?"

"Niltze?"

"Huh, wait, but does the Nile really exist? Here too? Do the things I know actually exist? That salt lake I wanted to see it before I died..."

"...What are you saying."

The child spoke again.

"Why are you going this far?"

"Didn't we already go over this earlier?"

"Aren't you afraid of dying?"

Instead of answering the question, A-Qing talked about something else.

"Kid. Imagine you wake up and find yourself turned into a hella handsome man. Stunningly so."

"What are you even saying?"

"Lets just say that's the case. Just consider it a dream. But in this dream, you don't wake up. You get hungry, you eat, you get sleepy, you get hurt. Then, is that really a dream?"

"Then it's not a dream."

"But then, there's this Status Window, no. Uh..Yeah, there's like this ghost following you around. While following you around, it constantly tells you. You're dreaming right now. This is a world inside your dream."

"Then, is it a dream?"

"I don't know. Thats the problem."\footnote{Most likely a reference to 'The Butterfly Dream' from The Zhuangzhi texts.}

A-Qing bit her lip.

Every time she went to bed, she imagined waking up to her comfortable studio apartment.

A production worker, having fallen asleep at his desk, would wake up groggily and chuckle at the sight of the character he just created on the screen.

He might delete the game out of discomfort or he might just shrug it off and enjoy it.

Since she had come here so suddenly, it wouldn't be too strange if she returned so suddenly too. Right?

So, A-Qing lived recklessly.

She lived as she pleased and spoke her mind.

\textit{Because in a world where leaving at any time wouldn't be strange, why should I care about other's opinions?}

So, A-Qing did not hold back.

There was no reason to save money.

What was the use of hoarding money, buying a house, and stacking up gold? Wouldn't it all disappear anyway when she returned?

Of course, this world was definitely reality.

A-Qing did not consider it as a dream.

At least, if only that damned Status Window didn't exist.

The Status Window was constantly telling A-Qing she was a stranger. A foreigner. An outsider.

That she was an existence that did not belong to this world. 

That she should not forget she was a game character.

{\itshape What happens when I die?

Do I just die? 

Will Game Over appear and will I get a chance to retry?

Or will I just return in front of a monitor?}

Since she was dragged into this world without a reason, being sent back without a reason wouldn't be strange either.

{\itshape But what if there was a reason for being brought here?

What if some transcendental being had a purpose for throwing me into this world?

And then, what if that purpose no longer applies, whether I succeed or fail?

Then, what about me? What would happen to me?}

"...Are you okay?"

A-Qing forcefully steadied her wavering, unstable mind.

Now was not the time to throw a fit and screams.

"Of course. Obviously. Totally fine."

"You're sure you're fine, right?"

"You little shit. Who's worrying about whom?"

A-Qing tried to force a smile.

It wouldn't be visible in the darkness anyway, though.

In the end, the problem was people.

Was a life of just eating, sleeping, and shitting truly living?

Ultimately, people lived as people.

{\itshape I was so lonely. So very lonely.

And because that loneliness was unbearable, I eventually made a friend. And at the same time, because I'm an outsider, I eventually had to leave.

Because I didn't want to be hated, I accumulated Righteous Karma and played nicely.

And because of that, I meddled like this.}

"Excuse me."

"What."

"But, why did you bring me along?"

"Because I felt like it. What about it."

"Wasn't there a reason for it?"

"Well, I mean. If I had to choose one person, you were the only innocent one, after all. "

That's just how it was.

If she had to choose someone, she might as well side with the innocent.

After all, whether it was scammers or child molesters, they were all the same. 

"That Pure Yin Body or whatever. It's not like our little kid wanted to be born like that. You didn't say, 'I'm going to have a Pure Yin Body! Pure Yin Punch!' and then shot yourself out of the womb. It's not your fault that things just turned out this way."

It was also a message to herself.

{\itshape Was it such a crime to play games? Was creating a female character such a sin?

Things just turned out this way. What else could I have done?}

"But, Mom and Dad, too.."

"I'm sorry to say this, but your mom is a scammer, you know? Honestly, if she scammed a thousand gwans of gold, shes' a huge scammer even among scammers, right?"

"But, Mom and Dad did it for m-"

"Did you ask them to? 'Mom, please scam people for me. Otherwise, Mom's daughter will die.' Did you say something like that?So what crime have you committed? Nothing. Not guilty. Bang, bang, bang. No objections."

"But, those people-"

"No matter what sob story they try to sell, they're just child molesters, exploiters of minors, and whatnot. They're the scum of the earth. They can eat shit for all I care. "

A-Qing said this firmly.

Chen Changming squirmed in A-Qings embrace.

"Is it really okay?"

"Eung."

"Really?"

"Yep."

"Really, really?"

"Yeah."

"Really, really, really?"

A-Qing frowned at a sudden thought.

"Come to think of it, you're sixteen, aren't you? But what's with that? Are you pretending to be cute? Aren't you secretly enjoying being a kid?"

"...What are you saying. Ugly."

"You know, I didn't say it outright before."

A-Qing let out a snicker, before continuing.

"But honestly, youre not all that pretty yourself."