\chapter{Change the Course to North by Northwest (2)}

A-Qing received a massive shock.

The favor she had for her turned into bubbles and disappeared.

Was this how the Prince felt when he saw the black Little Mermaid\footnote{The controversy about The Little Mermaid live-action} after going through so much trouble to find her? Did he also feel as if he himself was the one who had turned into bubbles and disappeared?

"Oooooh, what's with our little brat? When you're hungry, I'm a beautiful Sister, and now that you're full, I'm ugly? Is that it?"

"Tch. Sister? What a joke."

"I apologize, Great Expert. This child wasn't like this before, but she become a bit strange since last year. I don't know why she's acting like this. Haiya."

Last year? Then fifteen. A 2nd grader in middle school.

A-Qing was suddenly convinced.

\textit{Puberty? That's a given. Mhm. Yep.}

However, the mother seemed to have quite a bit on her chest.

"She suddenly doesn't listen. And honestly, it would be a relief if thats all she did, but now she always does what she's told not to. I mean, it is understandable to hate her mother. A woman who has nothing to pass on and wasn't even able to give birth to a healthy body..."

"AH! Stop talking nonsense like that! Its so annoying!"

Chen Changming shrieked before running up the stairs.     

Thanks to that, A-Qing was left feeling awkward alone with a heartbroken mother.

"Uh.. So. Would you like a drink?"

"Then, I'll have just one, in spite of my shame."

"Oh, it must be hard for you."

"Hard? Of course not. It must be because the mother is so worthless that the child ended up so pitiful. Because I couldn't even give her something so ordinary."

Yang Xiaoyue lifted her glass with a sorrowful expression.

She took a drink with a familiar gesture full of grievances, then covered her mouth and wiped her lips with a handkerchief.

Yang Xiaoyue's expression hardened as she lowered her voice.

"Excuse me, Great Expert."

"Yes?"

"Be careful. The alcohol is poisoned."

"Eh?"

Yang Xiaoyue sneakily showed her handkerchief.

It was wet with the liquor she pretended to drink but spat out.

A-Qing looked back and forth between the handkerchief and the glass, then suddenly gulped down the liquor.

"GREAT EXPERT!? WHY!?"

"Keuuuu. That's the shit. Haiya, it sticks to the mouth."

Spiciness arose faintly in the aftertaste.

Despite the numbness as if her mouth was paralyzed, there was a distinctly burning spiciness.

The numb taste was Ma. The spicy taste was La.

Combined, it was the taste of Mala!

The taste most loved by the Korean people.

A taste enjoyed by their ancestors since ancient times.

It was a taste of tradition that was even depicted in Soo Bahk Do.

Wasn't this..the intended flavor?

{\itshape I thought the alcohol would taste like Mala, seeing as it was from an original Mala restaurant.

To think that it wasn't a culinary spot known for their good Mala!

It's fine because of my Constitution.}

When making her character, A-Qing followed the recommendation post.

She distributed Ability Points, chose a Star of Destiny.

And also selected a Constitution.

The Constitution A-Qing chose was Blood Poison.

A-Qing didn't know since she hadn't played the actual game, but originally, the AI of Wulin Chronicles: A Tale of Life and Death heavily used poison. Moreover, the UI was also quite inconvenient.

Needlessly, there were over ten types of antidotes, which were expensive, and with only four Quick Slots, dealing with poison was more than just annoying. It was a pain in the ass.

Blood Poison was a constitution that provided immunity to all poisons.

That was why it was recommended over cheat-like Constitutions such as the Heavenly Martial Body, Natural Body, or Nine Yin Blood.

As such, A-Qing was free from all poisons.

It was the secret to surviving that year, right after starting her Wulin journey; she managed to live off grass and mushrooms and even scavenged food waste.

A-Qings survival was the result of the efforts of sweats in the community of Wulin Chronicles: A Tale of Life and Death, who went to great lengths for newbies.

Furthermore, the miracle that A-Qing could read, write, and even communicate with the natives here was thanks to the Korean Language Patch.

That pure goodwill which hoped for their favorite game to be more popular and more people would enjoy it! 

That very goodwill was what kept A-Qing alive and breathing until now!

A-Qing suddenly shivered while recalling such things.

\textit{Fuck, Im never going to forgive the motherfucker who recommended this game. Seriously.}

A-Qing sprang up from her seat.

It was the time for her to fuck somebody up.

Oh how joyful it was to have someone to fuck up, all while having a justification to do so!

"Server!"

"Ah, Customer! Coming!"

The server ran out with a happy expression.

After all, a rich customer was a server's joy.

But even that was only for a moment.

The server's face was soon filled with sorrow.

After all, anyone would be filled with sorrow if the tip of a blade touched right below their throat.

"You dare to poison my liquor? You're fucking dead today. When you go to hell and your parents ask why you're there, tell them you died early because you were fucking around with someone else's alcohol."

A-Qing lowered her voice. 

"Oh no, no, Customer! No! It wasn't me! It really wasn't me!"

"You're saying it wasn't you? Then who was it?"

"Well, that is..."

A-Qing saw the server's Karma.

The number was 42. Unfortunately, he had Righteous Karma.

Why does the server, of all people, have such high Righteous Karma?

Did he feed the local shithead beggars or something?

A-Qing was lenient towards the virtuous.

"Alright. I'll believe it wasnt you. Then who told you to do it?"

"Haiya, that's..."

"Did the alcohol get bored and turn itself into poison? Or did the person who made the liquor get so bored that they decided to poison a bottle and sell it, hoping someone would die?"

The server gauged her reactions nervously.

A-Qing then offered a metaphorical carrot.

"From what I can see, Server, you seem to have a good nature. So, I trust our server. That means someone must have ordered you, right?"

Of course, there was no such thing as a server with a shitty nature.

If there ever was, it would only be due to unfair labor, like an angry innkeeper's son.

"P-Please s-spare me! I was just..."

"Argh, I'm getting angry! When I'm angry, my hand shakes! What if I accidentally cut off our innocent server's head!"

"P-Please, please s-spare me!"

"No, I won't spare you. I don't have any intentions to. Speak quickly."

The server sobbed.

A-Qing really didn't want to see the hot tears of a middle-aged man.

"DIE! You sons of bitches who dared to fuck around with food! My Moonlight Sword is starving!"

A-Qing leaped forward.

Towards the men at the inn's corner, who only had a few lousy dumplings on their table. 

One head soared into the sky and blood spurted out like a fountain.

A-Qing, drenched in the warm blood, grinned and continued her sword strikes towards the enemy of her alcohol.

As expected of cowards who resorted to poison, their skills were pathetic.

Three corpses and one soon-to-be corpse remained.

The man clutching his stomach spat out blood and spoke.

"How did you know...?"

"Well, everyone else was watching with fascination, but you guys were the only ones looking around nervously."

The man asked back incredulously.

"That's it? What if you were wrong?"

"Well, even if that wasn't the case, you were bound to get stabbed and die anyway. You guys have gone around doing a lot of bad things, havent you? If I was correct, revenge successful. Even if I was wrong, I would still be taking out the trash. Its a win-win."

They were bastards who had stacked up an immense number of Evil Karma.

If they weren't the culprits, oh well! She could just consider this as a virtuous deed.

A-Qing was in a situation where there was no loss for whatever choice she made.

"So, what poison did I drink?"

"Kekeke, you think I'll tell you? Now that it's come to this anyway?"

"Whatever then."

{\itshape I was asking because the taste was surprisingly decent, but oh well. He doesn't want to tell me, so what else can I do except move on?

  Goodbye, my Mala sauce.}

A-Qing hadn't really expected an answer anyway.

\textit{  Well, I'm sure it'll come out later when I looted his corpse.}

And with that, A-Qing lifted her sword.

"When you go to hell, they'll ask why you come."

"I'll tell them I came to fuck your mother."

His words were quite venomous for a dying man.

A-Qing sighed and swung her Moonlight Sword (No. 6).

"Keheuk? Grk, grk."

If the windpipe is precisely cut while avoiding the arteries, a person would not be able to speak.

The man clutched his throat, but then his guts spilled out, so he grasped his stomach again.

And as he did so, he finally realized why humans had two hands.

"Well then, you saw that, right? How he cursed my mom? So, let him die. If anyone touches him, I'll take it as you wanting to have a nice, little, friendly sword fight with me."

While looking around left and right, A-Qing issued a veiled threat without hiding her bright smile.

But something was strange.

{\itshape  Why are their Karmas all like this?

  Is this an inn where only bad guys gather?

  Burning down the entire place would probably accumulate a lot of Righteous Karma, wouldnt it?}

However, A-Qing wasnt a crazy bitch who shouted 'I will immediately cut down all evil' and start swinging her sword at every villain in her sight.

She just believed that anything goes when it comes to dealing with evil people.

Well, first things first.

A-Qing hummed a tune while rummaging through the bodies.

Was it perhaps because they were bastards who ate dumplings? They turned out to be broke as fuck.

Instead, various miscellaneous items were found.

A few small porcelain bottles, a pouch filled with powder, etc.

After efficiently gathering everything and returning to her seat, A-Qing met Yang Xiaoyue's wide-eyed, trembling gaze.

She realized her mistake. Oopsie.

"Server, bring some water so I can wash up."

It did feel nice when she was covered in blood.

And though this may obviously be common sense, some unfortunate souls might not be like her; they might fear blood itself.

If that was the case, didn't they just need to overcome it with ox blood soup?

{\itshape  But wait, does Wulin even have ox blood soup?

  I wanna eat ox blood soup."}

Following this oh so natural flow of thoughts, A-Qing smacked her lips before tipping the liquor bottle into her mouth.

One more glass to pat herself in the back for completing another worthwhile deed today.

And another glass to enjoy while watching the life ebb away from the evildoers.

The side dishes were good, so the alcohol flowed down her throat easily.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Yang Xiaoyue could not come to her senses.

In truth, genuinely skilled female martial artists were rare in Wulin.

Apart from those ladies who dressed up in fancy clothes and weapons for outings, that was the case.

To be fair, embarking on a Wulin journey in a women's body was often a dreadful hardship not chosen twice.

To put it nicely, they were called martial artists, but in reality, many were vagabonds.

After all, how could wandering outside of home ever be seen as a favorable situation?

In some ways, eating, sleeping, shitting, fighting, and even breathing outside was practically a humiliation for women. 

Maybe female martial artists from prestigious families could enjoy it as a sort of trip, with servants and carriages at their disposal.

There were also daughters from precious families who enjoyed acting like martial artists. 

But poor female vagabonds, who had no backing, would say those ladies were merely playing at being martial artists.

Yang Xiaoyue, hailing from Divine Maiden Sect of Mount Wu, despised such women who came around to roleplay as martial artists.

That was why she had a favorable impression of A-Qing.

Moreover, being kind to her child was something she was truly grateful for as a mother. 

Originally, real female martial artists were supposed to be rough.

Giggling among men would only make them look down on you, after all.

In Wulin, being underestimated was akin to walking around with half your life forfeited.

Yet even so, there was a limit to how rough and aggressive one should be.

Wasn't this practically the behavior of a madwoman?

Watching A-Qing wash her face in the basin that had just been brought out, Yang Xiaoyue resolved.

\textit{I really shouldn't get entangled with this child.}

However, that resolution didn't even last a day.