\chapter{Change the Course to North by Northwest (7)}

"Yes, I'm telling you that's how it is. The world is quite the perilous place."

A-Qing firmly stepped on the back of the rat-faced man.

"S-Save me! Please save me!"

Just as she was about to thrust the Moonlight Sword (No. 6) into him, Dao Master Shengsou urgently stopped her.

"Wait! Fairy. Shouldn't you still show him some mercy, even if he has sinned?"

"Huh? What? Why? Using these kinds of things as fertilizer is the only way to benefit the world, though."

"It is all for your sake, Fairy. For those who walk the path of Dao, accumulating a karma of killing does no good."

A-Qing waved her hand dismissively.

"Ehhh, nah, I'm fine."

A-Qing plunged her sword into the back of the rat-faced mans neck with precision, eliciting a bitter smile from the old Daoist of Wudang.

A-Qing swung her sword to shake off the blood.

A graceful sheathing of the sword followed.

She had practiced this move a lot when there was nothing else to do.

"But Elder, why did I get hit? I vomited a whole bowlful of blood. And this friend over here has not apologized even once."

"Hoho, Lu".

"Teacher! But I really saw it with my own eyes! Clearly! Exactly! It was a sight of unorthodox, evil, deathly Qi oozing out of her eyes! So purely evil that it has no comparison! I swear on the honor of Teacher! There is not a shred of falsehood in my words!"

Huanlu leapt up in indignation.

This was one of the strongest types of promises among martial artists.

'I swear on my sect that it's true.'

'I swear on my Teacher that it's true.'

It was much more solemn than its modernistic counterpart where one would swear on their mother.

It was because lying on the name of ones sect or teacher could lead to expulsion and the dishonor of being cut off from ones lineage.

And a single expulsion could ruin a martial artist's life.

As such, this was far more serious than the modern era, where one could go 'Imma shit on my family once. Sorry, Mom!' and pass over it.

"Hoho, Lu. What should I do with this punk."

"I am telling the truth! Do not be fooled! She must be some Yaoguai\footnote{妖怪. More populary known as Yokai }!"

"Lu, where in this heaven and earth would there be Yaoguai? How can someone who cultivates the way of the Dao speak like a charlatan?"

\textit{Eh, charlatan?}

A-Qing tilted her head.

\textit{Isn't charlatan an English word?}

Actually, charlatan came from a word used by Confucius, which had a similar meaning but was not exactly the same.

It basically meant something equivalent to a counterfeit or knock-off.

As A-Qing pondered this, Huanlu, filled with grievance and feeling wronged, was seething. 

"No, Teacher! In this Trichiliocosm, how can there not be such capricious and mysterious monsters!"

"Oho, this punk, who is as blind as a bat, dares."

Dao Master Shengsou's beard bristled.

However, Huanlu seemed a bit more oblivious and lacking in tact than usual because of his excitement.

"Why? Didn't you previously say that evil spirits and demons akin to Living Jiangshis are made-up tales that only exist in the Classic of Mountains and Seas! But how did that turn out! Wasn't I right before! Beneath Dongting Lake wasn't there the Living Jiang- "

"You rascal! Do you need a caning to set your mind straight!"

"Hup."

A secret history of Wulin slipped out from Hunalu's mouth, as light as a feather.

However, A-Qing didn't know anything about it anyway.

\textit{Living Jiangshi?}

\textit{Weren't Jiangshis those corpses that stuck their arms forward and hopped around?}

\textit{But if a Jiangshi was alive, wasn't it no longer a Jiangshi?}

\textit{Well, what do I know. I guess that kind of thing exists.}

A-Qing got to the point.

"Elder? Anyway, it seems he has no intention of apologizing."

"I am truly sorry to the Fairy."

Dao Master Shengsou spoke as if he was ashamed.

A-Qing responded with a smile, as if to indicate it was okay.

"In return, how about we go do a good deed together?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A-Qing roughly explained the situation.

This child was being targeted, but needed to reach Mount Wu. As such, she was bringing the child, but it seemed like they would continue to be attacked by such people.

Dao Master Shengsou nodded willingly, having clearly heard the rat-faced man mention kidnapping before he died.

If the destination was the Divine Maiden Sect of Mount Wu, it wasn't even a detour. It would only take about three or four days at most. 

Moreover, if it was the Divine Maiden Sect.

Even if it was considered a mysterious sect that existed outside worldly affairs, it was still a legitimate Daoist sect.

And Daoist sects were like distant cousins to each other.

They did not necessarily need to know each others faces to feel connected.

In addition, Huanlu really did get hit with a stick.

The punishment focused more on shame than pain.

Was it perhaps because of that? The teacher's caning had no effect whatsoever!

"You demon, I now know your identity."

"My identity? That's interesting."

"Demon, you are the very nine-tailed fox that seduced King Zhou of the past and soaked the Heavens in blood. You must be a Jiuweihu \footnote{'Fox spirit/ demon'. Gumiho in the original text}. You might have bewitched my teacher, but don't think for a second that you can fool me."

"What is this guy saying? Is he a lunatic?"

"You are truly horrific. A demon that wears human skin and mimics them. I clearly saw the endless malice pouring out from those sinister eyes with my own two eyes."

It seemed he was quite aggrieved about being whipped in front of everyone in broad daylight.

A-Qing chuckled and raised her voice.

"Elder! He is spouting bullshit again!"

"This cur really can't come to his senses, can he!"

"Teacher! I feel wronged! This is unfair! That fox!"

"I see. I understand now. Even if it means breaking every branch in the mountains and streams I have traversed today, I must correct your delusion."

"EUAAAAAH, YOU DEMON! I WILL NOT FORGET THIS GRUDGE!"

Huanlu screamed as he was dragged away.    

Honestly, it made sense.

After all, Huanlu had seen correctly.

But since one could not see their own appearance, A-Qing, too, was unaware of what she looked like.

Moreover, mirrors were not as common in Zhongyuan as they were in the modern era.

Bronze mirrors were affordable but difficult to maintain and did not reflect clearly, while mirrors made of silver or mercury, even those the size of a palm, were treasures that cost a fortune.

A-Qing, being a wanderer, was far from such treasures.

She had rarely seen her own reflection fully.

As such, she ended up thinking, 'He is a bit special for a Daoist Monk, isn't he?', and left it at that.

Meanwhile, the sight of an elderly Daoist Monk with white hair hitting the calves of a grown disciple was a rare pleasure for the Daoists of the Wudang Sect.

After the Daoists hurriedly followed out, worried they would miss such a spectacle, A-Qing asked Yang Xiaoyue.

"Uh, Mother. Do you perhaps know about Hao Sect?"

"Hao Sect...you say?"

"The bastard with the rat face said he was from the Hao Sect. I don't really know about it, though. Are those guys famous?"

"That..."

Yang Xiaoyue hesitated before answering.    

"...I am not sure either. I am very sorry I cannot be of help to our savior."

"Nah, don't be. Why would you? There are so many something something sects and something something factions in the world, after all. How could you possibly know them all?"

But it still nagged at her.

It was her first time encountering someone using bombs.

{\itshape No, like...why were there bombs in martial arts fiction? Why is it even a thing? 

At this rate, cannons and guns gonna appear too.}

Back then, she was out of her mind in her anger, but when thinking back, it was quite a chilling situation.

Moreover, from her experience dealing with various evil individuals, there was a slight difference in the way he presented their backgrounds.

\textit{Is it confidence? Or should I say pride?}

A-Qing scratched her head.

It seemed her mind was wandering now that she was a bit comfortable.    

And make no mistake, traveling with the Daoists of the Wudang Sect was indeed comfortable.

There had been a couple of ambushes, but the Daoists swarmed out and before A-Qing could do anything, they had already taken care of it.

Moreover, she hadn't felt the urge for blood lately.

As such, she just comfortably observed.

Also, Female Middle Schooler-chan seemed somewhat distant.

How should she put it? It was like there was this sense of alienation or distance between them.

She wasn't sure if she had made a mistake somewhere either.

Thus, they approached Mount Wu without any major incidents.

Until about four days away from Mount Wu though, a group blocked their path.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Initially, A-Qing wasn't particularly concerned. Nor did she pay attention.

It was unlikely that attackers aiming for Chen Changming would brazenly block the road. And in the first place, considering their Righteous Karma, they didn't seem like bad people.

A young man standing in front of the group blocked the way.

His Righteous Karma was 62.

It was just that Dao Master Shengsou had heightened her standards. In reality, this was among the highest she had ever seen.

Dao Master Shengsou, Little Supreme Justice, and now, this young man.

As long as they did not exceed three digits in Evil Karma, it meant they weren't going around doing bad things.

As such, A-Qing was at ease.

"Ah, you are experts of Wudang. Could you perhaps be Dao Master Shengsou?"

"Hoh, do you know me?"

"I am Caiwu of the Yang Clan."

Oh, A-Weichi, no, I mean, Great Expert Yang Weichi's son! The last time I saw you, you were about this tall. Your face looks the same as it did then. And you still remember an old man like me! How impressive!"

Listening in, A-Qing assumed it was a greeting to a friend of his father.

Consequently, Dao Master Shengsou was also smiling warmly.

"Yes, yes. Well, how is the Great Expert? No, wait, I heard he went into closed door seclusion. Is he still training?"

Yang Caiwu's expression darkened.

"In truth, Father did not enter closed door seclusion."

"Then what happened?"

"He was severely injured while fighting the Demonic Cannibal."

"What! Then, what's his condition?"

"He was in a state where his life could not be assured, but fortunately, there has been significant improvement recently. He has regained consciousness."

"Oh my, oh my. What a relief. We almost lost a giant of the Orthodox Faction."

Dao Master Shengsou patted his chest in relief.

And then, he continued with a tone filled with sympathy.

"Ah, you should have at least sent word. If the Divine Hero of Changan was the one in critical condition, the Sect Leader would have spared no effort. He would have given Purple Night Pills without any hesitation."

"It was due to a vehement Demonic Arts. The Divine Doctor said that an elixir would only act as a poison."

"Ah, I see the Divine Doctor attended to him. That is fortunate! Truly fortunate."

"However, the Divine Doctor mentioned that his Yuan Dan was damaged by Flame Demonic Arts."

"Flame Demonic Arts! How was he afflicted by that cursed Demonic Art!"

Flame Demonic Arts!

The name caused a stir among the Wudang Sects Daoists.

A-Qing, not knowing what it is, just listened.

After all, it wasn't her place to interrupt their discussion.

{\itshape But what exactly is Flame Demonic Arts?

Does it involve shooting fire from their hands or something?

That sounds.

Pretty cool.

Come to think of it, there's also a Mount Hua Sect, right?}

Even A-Qing, the Martial Arts Fiction Ignoramus/Wah-Wah I Dont Know Shit About Wulin, had heard of it. 

{\itshape Flame Demonic Arts, you say?

If lava beats fire, does that mean the Mount Hua Sect is stronger?}

As A-Qing was lost in meaningless thoughts, the conversation continued.

"The Yuan Dan is damaged? And elixirs doesn't work? My word. Then, what can be done? Is there a way?"

Dao Master Shengsou pressed on, his expression turning somber upon hearing the news of his friends critical condition.

"...There is a way."

"Oho! How fortunate that there is! So, what is it?! Is there anything I can do to help?!"

"Apparently, there is only one treatment in this world..."

Yang Caiwu trailed off, his gaze shifting towards A-Qing.

Or to be more precise, towards Chen Changming standing beside A-Qing.

\textit{Wait, something seems terribly wrong here.}

A-Qing felt a deep sense of foreboding.