\chapter{Change the Course to North by Northwest (3)}

Everyone had a plan. Until they got beaten the shit out of.

A-Qing also had a plausible plan. 

Let the record show that she drank poisoned liquor.

First, the fault was with those who, for unknown reasons, threatened the server and made him pour poison in her drink.

Next, it was the inn for their poor customer service and mismanagement of it's staff.

However, A-Qing did not blame the inn.

Because she planned to do so tomorrow.

After staying a night and having a late breakfast before her departure, she would order a table full of alcohol and dishes.

Then, she would enjoy a free feast under the pretext of compensation for damages before leaving.

There was a reason for A-Qings wicked plot.

First, it was because the innkeeper, though apologetic, did not offer to provide anything for free with his own will, thus finding him absolutely disgraceful.

Second, she couldn't risk asking for freebies right away as she couldn't be sure what they might do to her food tomorrow morning.

As such, she giggled herself to sleep, thinking about all the food that was going to meet their end in her stomach.

But haiya.

What was going on on such a pleasant night?

Clang, clang, clang. The sound of weapons clashing woke her up.

What's up with this noise between floors?

A-Qing closed her eyes again.

However, once one was aware of something, it was only human nature to focus on it; truly, the very definition of human sorrow.

Cling Cling Clang Clang Fun Games.

Boom Boom Kwang Kwang All Together Jump Jump\footnote{Crayon Pop Bar Bar (+Bar), a Korean song}.

Snap. A-Qing's last thread of patience broke.

After all, it was a patience that had become as fragile as overcooked noodle strands since the start of her Wulin journey.

A-Qing drew her sword and stormed out.

"YOU MOTHERFUCKING PIECES OF FUCKING SHIT! LET ME SLEEP! LET! ME! FUCK! ING! SLEEP! IS THAT HOW YOUR MOTHER AND FATHER TAUGHT Y- Heut."

Before A-Qing could finish her roar, a suffocating killing intent rushed in.

Her waist bent like a bow.

A blade grazed past her chest.

A-Qing straightened her pack, using the momentum of the recoil to throw a left punch. It struck directly under the attacker's armpit.

Crunch. The delightful yet ticklish feeling of bones breaking.

Heuk, a choked gasp. A bending waist.

At that moment, the Moonlight Sword fell vertically.

The blade sliced through the top of the head, down the forehead and nose, before lodging itself into the philtrum.

"Senior Brother!". An enraged cry.

A straight sword thrust followed. A-Qing grabbed the corpse by the neck and pulled. The blade protruded from the corpses solar plexus. A-Qing pushed forward immediately. The dead crushed the living as they fell.

A-Qing pulled out the Moonlight Sword (No. 6), now stuck like an axe in wood. Something dripped down between the split head. The red was blood, the white brain matter. The two blended harmoniously, turning into a pink hue. 

The person crushed underneath screamed.

How noisy.

A-Qing stepped on the corpse's waist and thrust her sword held in reverse into it's back.

Two bodies, double the thickness, double the satisfaction.

After a few more stabs into the floor, the screams stopped.

\textit{This bastard has no fucking guts, huh.}

A-Qing licked her lips and flicked her sword, shaking off the blood.

"What the hell is going on?"

Inns in Zhongyuan built in an shape had rooms on the outside, corridors and railing inside, and an open space in the middle for light.

From the corridor, one could see all three sides from up to down.

And under the moonlight, a frenzied swordfight was happening in every corner.

Truly the very definition of a struggle of all against all.

What was this?

Was this some unknown culture to someone in their second year in Zhongyuan?

Suddenly, A-Qing recalled that the inn was filled with bad guys for some strange reason.

Perhaps it was a culture among these evil individuals to set a day to kill each other. Right?

Then

- Ming!

Upon hearing that distressed voice, A-Qing swiftly turned her head.

On the first floor, there was a child wrapped and tied to a human figure; A-Qing dashed down the corridor and leaped over the railings.

A-Qing landed right in front of the abductor on both feet, one knee, and one hand. It was the so-called hero entrance\footnote{Marvel's three-point landing}!

The Moonlight Sword fell precisely into her outstretched right hand.

Under the moonlight, A-Qing slowly stood up.

"Ouch."

A-Qing endured the pain in her knees and palms.

\textit{This must be the agony of heroes.}

In truth, it was an utterly terrible landing method that did not distribute shock at all.

But that didn't mean it was ineffective.    

A dopeness that traversed over the centuries, leaping into the past!

The abductor took a step back, overpowered by it's momentum.

After all, although he couldn't gauge his opponents Realm, that one move certainly did look impressive.

"Release the child and disappear. Then, I'll spare your life."

A-Qing exuded Sword Qi. Swirls of Sword Threads wrapped around the blade; a demonstration of her martial prowess.

After all, even if it was A-Qing, she couldn't just slash at a kidnapper when he was holding a child.

After reading her countenance, the abductor suddenly threw the child.

The startled A-Qing leapt, throwing her body forward.

Fortunately, she managed to catch her.

Instead, with a \textit{Pshuk}, her arm seared with pain.

A dagger was embedded into her upper arm; only the handle could be seen, stiff and upright.

"I DID IT!"

A screeching sound. A-Qings head snapped around.

She locked eyes with the fucker who threw the dagger.

The bastard has turned his back.

And in the midst of it, he continued to scream.

"KILL HER! SHE'S LACED WITH THE SEVEN STEPS POISON, SO SHE WON'T LAST LONG!"

That motherfucker. Didn't he see me downing poison as if it was fucking liquor?

The shine in A-Qing's eyes dimmed.

\textit{I'm going to kill that fucker. I'm fucking going to kill him.}

But before that, there were other bastards trying to cut in line.

Like moths to a flame, emboldened by the Seven Steps Poison.

A-Qing stuck Chen Changming onto her side and threw her sword. While one bastard was distracted from deflecting it, her hand formed the shape of the Buddha's Hand.

Dingggg-! The sound of a bell ringing. One head near her exploded. The remains flew in all directions. Skin with hair attached, shattered bone fragments, brain matter, and two eyeballs with little tails dangling from them. 

Killing intent surged from her left. The kid was plastered onto that very side.

As such, A-Qing lowered her body and spun around two and a half times. Her accelerated foot hooked an enemy's ankle. The foe's two legs went flying.

With that, the enemy was sent flying straight due to inertia.

A-Qing stomped on the neck of the bastard and leaped forward.

A spear blade flew towards her thigh.

She caught the spear shaft. Right as she was about to pull, there was a sound that seemed to cut through the air with a swish. A massive sword blade rushed in.

A-Qing lay down on the spot, pulling the child into her embrace.

The enemy's sword blade aimed towards the ground. A-Qing rolled wildly to the side. Thud, Thud, Thud, Thud, the sound of the weapon hitting the ground followed A-Qing.

The dagger lodged in her arm dug further in.

It was so painful that she could not even scream.

\textit{The world is spinning and my arm hurts. It hurts so much. It hurts. It hurts.}

An ankle was caught in her hand. She clenched her fist.

The ankle was crushed under the grip filled with Qi. The bone splintered and broke, tearing through the skin and tickling her palm.

A strange heat rose quietly from her dantian.

The pain eased a bit.

A-Qing pushed away the falling owner of the ankle with her feet. 

The martial artist, who was about to slice down into the ground, tumbled along with the ankle cripple. 

A-Qing flicked her waist. With the rebound, she quickly stood up and extended her hand. Inner Qi swirled around furiously.

Dinggg-! The brutal fist and palm of the Buddhas Palm was unleashed. 

A headless body fell onto A-Qing.

She tucked the child by her side once again and all too naturally took the sword from the headless corpse.

"You're back, Moonlight Sword!"

A-Qing grasped the Moonlight Sword (No. 7).

The heat from her dantian spread throughout her entire body.

And in that moment, A-Qing lost herself.

Trance.

It was a fascinating experience.

She felt like she was warmly and comfortably lying down, resting within her body that someone else seemed to move.

A-Qing soon found the right term for it. Auto Attacks!

A-Qing walked out.

She felt good when she spun and stepped as if dancing. In fact, her attitude was almost one of a beautiful woman frolicking.

Sometimes she would circle far around to cut an enemys wrist, thus making a scream bloom, and the woman would shiver.

When drawing a circle, the scribble that swirled like a whirlpool pierced the heart, sliced the spleen, and cut the intestines.

A gentle touch drew a straight line, connecting ear to ear, and all too naturally, the head opened like a lid. 

With every step, blood flowed.

Life faded and the woman laughed.

Finally, in the center of the inn

Under the scattered moonlight, a female swordsman with a child stood alone.

It was only then did A-Qing regain control of her body.

A tepid fatigue pressed down heavily on her.

She nearly staggered.

\textit{What the heck! Take my body again. It was so comfortable earlier!}

"Ming!"

A blood-soaked Yang Xiaoyue burst out.

She was a reliable ally who kept throwing chopsticks whenever it got dangerous. In fact, that was much more helpful than a clumsy joint attack.

Yang Xiaoyue took the child and drew a sword to protect A-Qing's side.

Thus, the battle ended.

The inn was a mess of corpses and scattered limbs that had lost their owners.

And such owner's were those who groaned and clutched their wounds.

Some crawled around looking for their wrists and ankles and exhausted survivors watched A-Qing nervously.

"The party is over. Everyone, go home."

She said this with a smile, but in fact, it was a bluff.

Just as how it always was whenever A-Qing spoke kind lines.

She had no Qi left now.

In fact, it was hard to even straighten her trembling legs.

Generally the power of the martial arts was proportional to the consumption of internal force.

The Sword Art of the Yue Maiden was a peerless skill.

Moreover, the two manifestations of the Buddhas Palm played a role as well.

While all her Inner Qi Arts was inherently powerful, even among them, the Buddha's Palm was special. After all, it was the pinnacle of all Orthodox Martial Arts. As such, it was not meant for a martial artist at the mere Peak Realm to use.

The survivors were cautious, yet they still continued to gauge her condition.

A-Qing spoke again.

"Honestly, I'm not in a great situation either. But I can still take two out of three of you with me. One-third. How about it? Are the odds worth a shot? Wanna go?"

That statement produced a decisive result.

"We shall take our leave now. May we collect the bodies?"

"Leave the dead bastards."

"...Thank you for your consideration."

Some turned away in solitude, others collected their comrades bodies, and another spoke of vengeance.    

"I am Choi Beon of the Gangneung Subsect. You, bitch, will pay for this blood debt someday."

"Sure, whatever. You do that."

\textit{That loser talk too much. Given my temper, I would've liked to settle this once and for all, but the circumstances dictate}

A-Qing had to hold her ground for a long time until all the enemies had left.