\chapter{Change the Course to North by Northwest (5)}

Poor children matured quickly.

So did sick children.

And Chen Changming was both sick and poor.

Moreover, she wasn't even poor from the start.

When returning to her senses after collapsing from a fever, the decorations in the house were gone and the number of servants had decreased.

With that, the spacious manor had shrunk to a damp corner of a room with a creaking door.

Her dad, who went to get medicine, never returned.

Instead, only the medicine came back.

It should have been the other way around, though.

Her mom could not even properly grieve.

During nights where she pretended to sleep because she couldn't, she heard her mom quietly sobbing, fearing she might hear her.

Not long after, they left home.

It was all her fault.

That was why Chen Changming had to be a rude brat.

She had to be an immature child.

Having matured too early for her age, she knew that her adult-like demeanor would only hurt her mom, her mother.

And that was when she saw that woman.

A woman who set up an expensive meal and laughed foolishly with the happiest face in the world.

Something dark stirred inside Chen Changming's heart.

While watching her happily feast, she managed to get a bite.

And in the end, she fell for the provocation and ended up eating until her stomach nearly burst.

The food was delicious, though.

However, she couldn't stand it when her mother expressed her pathetic gratitude.

It was because she shouldn't need to do that.

After all, it was just a frivolous act of kindness from an idiot who thought the world was all happiness.

A truly shitty, cheap, and superficial favor.  

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

They were inside a slowly rolling carriage.

A carriage was originally an object that moved slowly.

If it went slightly faster, it became not a means of transport but a torture device that targetted the passengers buttocks.

Inside, A-Qing was having a hard time.

"Mother, is this really okay?"

"My child is a bit spoiled, so.. Ming, youre making the Great Expert uncomfortable."

"...This place is comfortable for me."

The comfort of a ride ultimately depended on how scientifically it could cushion impacts.

The carriages shock absorption relied heavily on the materials.

Meaning, it all came down to the elasticity of the lumber.

For that reason, Chen Changming wasn't exactly wrong.

A-Qing's thighs, moderately padded with a fair balance of muscle and flesh, offered a much more comfortable ride than any cotton-stuffed cloth.

In addition, it was also nice to lean her back on.

After last night's attack, Chen Changmings attitude changed.

She clung to her side and refused to let go.

Instead, A-Qing felt a bit uncomfortable.

If it were some ten-year-old kid, she could easily hug and caress them, showering them with affection.

But what if it was a prime of her youth, springtime of her life, sixteen-year-old Female Middle Schooler-chan, who was just a bit small and frail?

Just having her sit on her lap was enough to prepare herself for social death. The Clink Clink of them handcuffs.

Moreover, her mother was right there on the opposite side!

As such, A-Qing had no choice but to stiffen.

{\itshape  But come on, isn't sixteen really not the age to be sitting on laps and acting all spoiled? Isn't that way too old for her now?

  Or is it? Is this a normal physical and mental distance for girls?}

In truth, Chen Changming was currently enjoying that very reaction with the sensitivity typical of a sick child.

Though she didn't know why, she noticed that A-Qing found the contact with her quite uncomfortable.

As such, Chen Changming went a step further.

She grabbed A-Qings left and right hands and placed them on her thighs, stacking them together.

A-Qing stiffened like a rock.

This was absolutely fucked. SHE was absolutely fucked.

To others, it might look like a young woman holding her niece. But not to A-Qing.

The saying that what matters is the inside meant that the way each individual viewed the world was particularly important in this moment.

{\itshape  Look at A-Qing hiding the A-Qing Law\footnote{ACT ON THE PROTECTION OF CHILDREN AND YOUTH AGAINST SEX OFFENSES}

  Is this a green light? Shut the fuck up. Fuck no, its not!

  Eh? Look at A-Qing hiding.}

She couldnt think of any of the myriad modern memes she would usually recite in moments of discomfort or unease.

{\itshape You, who were in the throes of puberty until just yesterday.

  Since when did you and I become us?}

A-Qing was doing everything in her power to think silly thoughts.

"Great Expert."

A-Qing startled at the sound of the displeased voice.

The stiff face of Yang Xiaoyue appeared in her vision.

"I am innocent! As you saw earlier, this was not my intentio-"

"It seems I chose the wrong coachman."

Thankfully, it wasn't an inquiry about child molestation.

{\itshape  By the way, what's wrong with the coachman?

  Ah. The coachman is absolute dogwater at his job. I see.

I guess it does kinda feel like I'm becoming one with the ground.}

She could feel every grain of sand on the road through her butt. Seriously.

She had once joined a friend for a drive to celebrate his new car.

And she got carsick in less than thirty minutes.

That was how much influence the driver had when it came to the comfort of a ride.

The carriage is slowing down.

Yang Xiaoyue gripped her sword.

A-Qing was surprised.

{\itshape  Sure, it feels like the coachman is driving with his feet, but isn't using your sword a bit much?

  Or is this considered common sense in Wulin?

  Maybe in Wulin, theres a custom of beheading a coachman who can't drive well.

  What a harsh industry.

  Then how do novice coachmen gain experience?}

While A-Qing was still lost in her thoughts, Yang Xiaoyue suddenly shouted.

"Now!"

There was no time to stop her.

Yang Xiaoyue kicked the door open powerfully and leaped out.

She clearly wasn't telling her to just watch, so it must mean to follow her.

A-Qing also jumped out while carrying Chen Changming.

"Shit! They noticed!"

"Get them! Only the brat needs to be unharmed!"

An unexpected welcome party had crowded around.

Only then did A-Qing grasp the situation.

\textit{  The fuckers havent given up yet, huh.}

A-Qings hand reached into her clothes before shooting something out.

One of the attackers who was rushing in grabbed his eye and fell to the ground screaming.

  "AHHHHH!"

It was a scream so loud that his throat seemed to rip from the inside.

However, anyone would scream like that if a chopstick pierced through their eyelid and into their eye.

After last nights attack, A-Qing did a lot of reflecting.

She had become too complacent after gaining some confidence as a Master.

If her Inner Qi had been just a bit less, she wouldn't be breathing so easily right now.

As such, she spent some of the Free Practice Points she had saved up.

She had about thirty martial arts with a White Border, among which she upgraded two Inner Qi Cultivation Techniques to 10 Stars.

As they were the lowest grade martial arts, there was no 12 Star and Grand Star realm. Because of this, she wasnt able to gain any special abilities, but there was still about a 20\% increase in her total amount of Qi.

Furthermore, she upgraded one Hidden Weapon Technique to 10 Stars.

Three Birds One Chopstick.

It was a throwing technique that had the meaning of hitting three birds with one chopstick; given that it was a readily available Hidden Weapon Technique, it was hard to expect much from its power.

However, a Master of the West, Senior Wick, had become renowned for massacring a certain unorthodox gang with a pencil. With a fucking pencil!

As such, even a Third-Rate Hidden Weapon Technique became a whole different beast in the hands of a master.

Three Birds One Chopstick was a technique that used any readily available stick, so its power was originally low. 

Therefore, the exquisite principle of its use lay in unpredictably. Or to put it more poetically, it was necessary to distract from the east but attack from the west.

The hidden weapons kept flying towards the assailants eyes.

One bastard had already been made a cyclops and had collapsed.

The attackers made their preparations, raising their arms to block at any moment.

But when they did so, a low strike buried itself straight between their crotches.

The second victim couldn't even scream.

Instead, he clutched his lower half and foamed at the mouth.

A vile attack that cut off all future generations.

The attackers felt a creeping fear that sent shivers down their spine.

"How vicious!"

"A witch! It's a witch! There's a witch here!"

Honestly, A-Qing felt a bit sorry.

But what choice did she have in a life or death situation? She couldn't really have any inhibitions or discriminations in her methods, right?

Since she had incapacitated two with mere chopsticks, it made the investment of her Practice Points worthwhile.

A-Qing drew her sword. A menacing Sword Qi surged.

"A Peak Realm Master!"

"Fuck, you never said anything about Peak Realm!"

The bastards hesitated.

A-Qing was about to dash forward but only took a step.

The startled enemies quickly backed away.

A-Qing was conflicted.

\textit{  Is it okay for me to see blood with this kid clinging by my side?}

She had already practiced the art of fighting with baggage in real combat the night before.

And from the looks of it, there were no Masters among them, so there were probably no issues.

But what if it gave a great blow to the delicate and sensitive nature of an angsty juvenile?

Right then, Yang Xiaoyue leaped in with exquisite timing.

"Great Expert! Ming can-"

"I was counting on you!"

A-Qing shouted in excitement and joy.

Her hands were free. They were all fucked now.

Two suspicious men who had chased after Yang Xiaoyue were split in half with a single sword strike.

Their upper bodies separated, spilling their contents.

The enemies opposite of Yang Xiaoyue quickly scattered away.

That was when it happened.

"Stop!"

A rat-faced man came out as if going out of his way to assert his presence.

A-Qing recognized his face.  

"You! From yesterday!"

It was the bastard who threw a dagger and ran away yesterday.

"Thanks to him, A-Qing was forced to reenact a certain Guan Yu experience\footnote{Records of Three Kingdom, volume 36. Basically Guan Yu being absolute unit, getting open arm surgery while feasting and drinking with his men}.

All luster disappeared from A-Qings eyes.

I swore I'd kill that motherfucker, didn't I?

Even while facing such killing intent, Rat Face somehow kept his morale high.

And then, he raised his arm high, as if showing off something.

It was a hand holding something black, large, and round.

"Stop! Do you not see this? If you don't want us to all die together, hand over that brat and-"

But A-Qing had already lost her mind in rage. She had far surpassed any sort of rational thinking or negotiation.

So, obviously, she didn't see it.

Ding-! The bell sound of the Buddhas Palm. 

The area above Rat Faces wrist disappeared without a trace.

And the black, large, round thing was pushed by the impact, flying far away and-

The sound became a shockwave that shook the forest.

Trees swayed, dry leaves flew, and grass was flattened all at once. Birds took off in unison.

A slight earthquake that traveled through the soles of everyones feet.

Thunder Bomb.

A secret weapon of the central government and Wulin's worst nightmare.

The only countermeasure was Reinforced Qi Armor.

Even the remains of a Peak Realm martial artist wouldn't be found if caught in its explosion.

But A-Qing didn't know about any of that. Nor did she care.

She had already grabbed Rat Faces neck.

"You motherfucker. I told you I'd kill you."

"Keuk, youneversaidth-"

"I did, okay? In my mind. Desperately."

"What's that supp-"

When the carotid artery was pressed firmly, there was no difference between a novice and a Master.

Rat Face lost consciousness and slumped down.

\textit{I can't kill this bastard that easily now, can I?}

\textit{Well then, how should I kill him? What would be the best way? If someone is watching me, I want them to say I cooked the shit out of him, you know?}

\textit{But before that...}

A-Qings head snapped around.

Her bright smile and dead eyes faced the attackers.