\chapter{Change the Course to North by Northwest (8)}

"Madam, I regret that we have to meet this way, but time has already been greatly delayed."

Yang Xiaoyue was utterly pale.

A-Qing felt this was the first time in her life seeing someone so white.

Her hand covering her mouth trembled as if convulsing.

Her trembling legs made it seem like she was using all her strength just to stand.

"I shall not ask you any further about your disgraceful act, so please hand over the child now."

Yang Caiwu was polite and respectful.

That was also why he was so resolute. 

A-Qing stepped forward with a finger pointed in anger.

"Wait! I was staying silent until now, but this is ridiculous. How can you so boldly tell her to hand over the child? Is it your kid? If you take her, will you feed her just one meal and return her nicely or something? Just from hearing what you're saying-"

"Young Lady, you..Hooo.

Yang Caiwu rubbed his face.

He looked as tired as someone who hadn't slept for a week.

"You seem to be under some sort of misunderstanding."

"Misunderstanding? What misunderstanding? Fucking hell, you shitty perverts."

Just as A-Qings specialty, indiscriminate personal attacks, was about to continue-

Yang Caiwu's next words stopped her.

"We have already paid a sufficient price."

"...What?"

A-Qing turned to look at Yang Xiaoyue.

"I never heard anything about this, though?"

"The price was a thousand gwan\footnote{Korean unit of weight. 1 Gwan = 3730 grams. There's no Chinese equivalent} of gold. It was an amount prepared by selling the family's entire estate."

"Uh..."

"And just recently, I received a message from the bank. That the gold was all transferred to the Bank of Wanjin\footnote{Ten Thousan Gold}."

Large sums were managed by writing promissory notes.

Even if it is transported by cart, a thousand gwan of gold would take ten of them.

As such, the gold was sent to the bank first and a promissory note was issued in that name.

In fact, trading promissory notes was advantageous for the issuer.

If the other party didn't keep their promise, one could simply contact the bank to stop the payment.

However, the gold was completely handed over to the Bank of Wanjin.

The Yang Clan had now fully transferred all ownership of the gold.

"But you disappeared. So, we had no choice but to put a bounty. The bounty was five hundred gwan of gold, prepared by mortgaging the clan's business and manor. Now, we have even staked the future of our clan."

The total was fifteen hundred gwan of gold.

The Yang Clan of Xinchang\footnote{a county in the Zhejiang province}, a clan that held sway over an entire province, had gathered this sum with all their might.

"Either way, the gold was prepared to bring back the child. If Madam found a thousand gwan insufficient, we shall add another five hundred gwan. Isn't this enough to save one life with the.price of another?"

The last words were directed at A-Qing.

Only then did A-Qing look at Yang Caiwi.

She looked at his high Righteous Karma.

He wasn't some scum of humanity who would take a child and harm them for fun.

He was the son of a dying person.

A son trying to save his father.

While it may not be honorable to buy a life with money, the clan has offered all the sincerity it can.

A phrase from the Mission Window came to mind.
\begin{quotation}
	[Righteous Karma) Transfer the elixir to the rightful owner]
\end{quotation}

Yang Xiaoyue had sold her daughter.

A-Qing felt dizzy.

She had stepped in needlessly and ended up seeing such an ugly scene.

Then.

As Yang Caiwu took a step forward, A-Qing, without realizing it, grabbed Chen Changming's hand and pulled her back.

"Wait! Wait a minute! Stop! I said stop!"

If it were a matter where one person was dead and one person would live, like a heart transplant, A-Qing could have just walked away, albeit with a heavy heart.

However, A-Qing already knew the truth that Yang Caiwu deliberately did not mention.

She remembered the terrible story Yang Xiaoyue had told her.

Chen Changming wasn't just going to die.

She would be violated until all her Pure Yin Qi was taken.

The future that she faced was one of misery and harsh circumstances, only to slowly die after enduring unspeakable abuses and recoveries.

She now knew why Yang Xiaoyue had told her this.

It was because she wanted A-Qing to protect the child.

That hidden intention Yang Xiaoyue harbored was so wicked that even while knowing this, A-Qing could not help but to succumb to her wishes.

A-Qing looked at Yang Xiaoyue.

"If...If we can somehow return the money, then-"

"...The child, the child was sick."

"Ah."

Only then did A-Qing fully understand the situation.

Yang Xiaoyue had never intended to hand over her daughter in the first place.    

It was a scam.

She scammed a son desperately trying to save his father.

In order to raise money to save her daughter.

No parents named their child carelessly or thoughtlessly.

They chose the best words and meanings, as the first gift a parent would give to their child.

江命. Changming.

Live a long life.

What must the parent, who simply wished for her child to live a long life, have felt?

"Benefactor, I will not deny it. But, even if its just a cowardly excuse, had I not accepted the deal, what would have become of us? We had no other choice."

"That's..."

Initially, it would be a deal, and if refused, the swing of a word would follow.

It wasn't because Wulin was particularly cruel, but because the heart that tried to save a loved one was utterly merciless.

A-Qing didn't know what to do.

Then, Yang Caiwu's words were directed towards someone else.

"Dao Master Shengsou, my father has dedicated his life to the peace and safety of Wulin."

"That friend has indeed done that."

"Please help us. I know it is not right for me to ask such a difficult request. But I do dare to do it."

"You..."

"Even if this against the laws of nature!"

Yang Caiwu shouted.

"Then, I speak of greater good! The Demonic Cannibal has mastered the Flame Demonic Arts! The wicked Blood Cult has already seized half of the East Sea! With the life of this one child, we can save thousands, tens of thousands suffering! Am I wrong!"

"...Oh, Heavenly Lord."

Dao Master Shengsou clenched his eyes shut.

"Fairy. Please hand over the child."

"Teacher?"

"Didn't you see it too? The lifeblood of a hundred people goes into a single Living Jiangshi. It was impossible to know where those lives came from. But now I understand. Since the authorities turn a blind eye to even the marauding foreign invaders, even if the villains disguise themselves, we have no choice but to helplessly let them run amok."

Dao Master Shengsou tried to persuade A-Qing.

"Fairy, recently, Wulin has been in chaos and there is no place below the Heavens without evil. Every piece of news entering the Wulin Alliance is urgent, leaving no one to lend a hand because they themselves are in search of their own salvation."

"Even if you say that to me-"

"The Yang Clan is a pillar of Wulin, guarding the East Sea. When neither the Nine Sects nor the Noble Clans can help, someone must stop Blood Cult evil deeds. And I am far too aware who is the most willing to shed blood in the very forefront."

When he said so, Yang Xiaoyue abruptly knelt and prostrated on the ground.

She bowed in the most humble posture imaginable, rubbing her hands together like a fly, pleading with her knees, chest, and forehead touching the ground.

"Great Expert Yang, please. I will do anything, endure any humiliation, even if it takes my whole life. Please have mercy on this child. Please."

Dao Master Shengsou, the Daoists from Wudang, Yang Chaemu, and the warriors from the Yang Clan of Xinchang all looked at A-Qing.

What's with this atmosphere? Why are they all looking at me?

{\itshape Just make a decision amongst you guys and let me know.

What? Am I the one to decide or something?

Do I have to make the decision?

Like what? If I make a decision, are you just gonna say okay and move on?}

A-Qing tightly grasped Chen Changmings hand.

And when she did, she felt a wriggling sensation in her grip.

"I'll go."

In a moment, all sounds of breathing in the area halted. 

"It is all because of me. Dad passed away. Mom, I...actually knew everything. Mom, you should stop worrying about me and live comfortably. If only we had done this earlier, Dad might have still been alive. It's all my-"

Chen Changming choked up.

"Go somewhere nice, hic, and just remarry. Instead of a crippled daughter like me, give birth to a healthy child and live happily."

"Ming!"

Yang Xiaoyue crawled on the ground towards her daughter.

Her trembling hand reaching out with all her effort was harshly rejected by the child.

"No! I hate it! I hate it too! I'm sick of living as a burden! I never wanted to be born like this! Eugh, uah.."

In the end, Chen Changming burst into tears.

Any and all crying in the world was ugly. It couldn't be helped.

The tale of a pretty expression with a single tear drop was a lie only found in stories. 

The child cried with a harsh sound, scratching her throat in anguish.

Yang Xiaoyue was beside herself and the Daoists and warriors couldn't bear to even lift their heads, shaking them instead.

And A-Qing made up her mind.

Once she did, there was not a single ounce of hesitation in her actions.

“Fuck, seriously! This is fucking hilarious!”

Everyones gazes turned to her.

"Look at everyone sitting here filming some sort of fucking melodrama. All of Wulin is in shock and the Emperor expresses respect! This is why the fucking Chinese people can't do it. The thing I hate the most in the world is racism and the close second is the fucking Chinese bastard."

A-Qing tucked the child under her arm.

"I don't neeed any of that! I'll be the one to eat up this kid. I'm going to be the one to fuck her and reach the Transcendent Realm, so if you have any complaints, keep them to yourself.

A-Qing looked around at everyone.

Every single one of them had dumbfounded expressions on their face.

Finding it hilarious, A-Qing laughed like a crazy bitch.

Then, in an instant, she straightened her expression.    

A-Qing stomped off the ground.

An amazing anti-gravity leap of the Yue Maiden Footwork unfolded.

And then, only her voice, gradually fading away, could be heard.

"This child is now mine! I can do whatever I want with her! Im leaving. Bye, everyone! No more shakles and restraints! I'm off to find my own happiness! I wish you all happiness too!"