\chapter{Change the Course to North by Northwest (9)}

People would be more likely to freeze up when they become too startled.

He didn't anticipate that the conversation would be concluded by a crazy bitch, so he wasn't able to grasp the situation quickly enough.

However, Yang Caiwu was desperate enough to have already prepared for such situations.

Of course, that did'nt mean he expected someone to suddenly claim the child as their own and kidnap them.

He just thought that someone might pity the child a bit too much and step in a bit.

From behind Yang Caiwu, a shadow slipped out from under the shade of the tree.

It was a person dressed in a black outfit made for the darkness of night.

The identities of those who moved silently and covered their face could only be one.

Assassins.

"Client, shall we begin?"

"Go and do what you have to do."

"What about the woman?"

"It doesn't matter. As long as the child is unharmed."

"Yes, understood. Of course."

The man in black blew a sharp whistle and ran towards the forest.

In response, whistle sounds echoed from both afar and near.

Soon, a small flame sprouted somewhere in the west.

"Descendents of Xinchang, if you do not like dishonorable deeds, you are free to leave now. But if there is anyone who wishes to remain as a spear, even if it means rolling in the mud."

Yang Caiwu nodded to Dao Master Shengsou.

And then, he stepped forward and spoke.

"...Follow me. Let us go."

None of the warriors from the Yang Clan responded.

They simply followed their Young Lord in silence.

They were the warriors of the Yang Clan of Xinchang, who had stood against foreign invaders, Japanese invaders, in the East Sea for a century.

Their own friends, parents, and even their friends.

There was no one who did not owe a debt of gratitude to the Yang Clan and they served with pride in that gratitude. 

"Teacher."

"Let us go our own way. Even if their purpose goes awry, we must find a way to help a Noble Clan that has silently dedicated themselves to the world."

Thus, even the Daoist Monks of Wudang left this place.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A-Qing became cheerful.

She decided not to think too much about it.

{\itshape Look at how comfortable it is when I just do whatever the fuck I want. They can suck my fat fucking cock.

Though to be fair, I don't have a dick anymore.

But hopefully, we will meet again someday, ay Cock?}

Chen Changming, who was crying and making a fuss while struggling to be let go, had eventually gone limp.

She seemed to have resigned herself.

What can she do about it anyway? She's just a brat, after all.

Then, an abrupt question came.

"...Are you really going to fuck me?"

A-Qing was horrified.

"Hey, shush! You're going to send me to jail. No bad words! Changming'er is a baby. You should only use good words."

"What are you even saying. Ugly."

"Well, if you say so, I guess I must be."

"You're ugly."

"Yes, I've taken your oh so valuable opinion into account. Anything else to add?"

"Tch."

Chen Changming clicked her tongue.

And then, she asked again.

"So, are you really going to fuck me?"

"No."

A-Qing confidently revealed her plan.

"We are going to head to the Mount Wu Faction!"

"It's not the Mount Wu Faction, its Mount Wu Sect. Mm? Wait, no, that's not it either"

"Whether it's Mount Wu Faction or Mount Wu Sect, who cares! Anyway, were going!"

One could practically hear the sorrowful cries of the Divine Maiden Sect.

"But why? Why say all those bad words and kidnap me?"

"What kidnapping? Let's call it a temporary relationship under unilateral coercion."

"...? Isn't that just kidnapping?"

"If I kidnapped you, you wouldn't know were going to the Mount Wu Faction, right? Our Changming doesn't use her head, does she?"

"What are you even talking about?"

"But there's one big problem."

"...?"

"I don't know the way. Where is the Mount Wu Faction?"

"...?"

"I said, I don't know the way. Do you know, by any chance?"

"Roughly. Northwest."

"Nice! Change the course to north-by-northwest\footnote{North by Northwest, a film by Alfred Hitchcock}!"

A-Qing casually changed direction and asked again.

"But where is the northwest?"

"The sun sets in the west."

A-Qing looked up at the sky.

The sky was full of dark clouds, as if it might rain at any moment.

"That's too bad. I was just a sliver too late. Kid, in order to make some prog- Kuk. "

A-Qing felt something tough around her neck.

Though her neck was caught, her body continued to move forward.

A-Qing flew about ten zhangs\footnote{Ancient Chinese unit of length. 1 zhang = 3.33 meters} in a straight line with her legs pointed forward and crashed to the ground.

Dry leaves crumpled around her as if exploding.

A-Qing quickly checked on Chen Changming in her arms.

"Hey, you good?"

"There's blood on your neck."

"Ah shit, it stings."

A-Qing rubbed her neck and frowned.

Fortunately, it only tore off a thin layer of skin. 

Instead, it was really goddamn painful.

"What kind of crazy bastard puts a rope in a forest? This is attempted murder, attempted murder I tell you."

"Too bad. That it only ended as an attempt."

An unfamiliar voice interjected.

A-Qing leaped up like a cat, startled.

She drew her sword to confront the enemy and was surprised again.

A figure clad in black, face covered.

There was only one conclusion.

\textit{Ninja? Since when are there ninjas in martial arts fiction!}

Nya! From nearby, a throwing knife flew.

It was thriftily taken from the corpse of the rat-faced man. 

The knife lodged itself in the neck of the person in black.

"Ehh?"

A-Qing made a dumbfounded noise.

She had been all nervous because ninjas suddenly appeared.

It was because if ninjas were the ones to ambush them, they were all supposed to die.

But what's this?

\textit{Ninja are no big deal, huh?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{...There was a time I thought that.}

It wasn't that \textit{a ninja} had suddenly appeared.

It was that \textit{ninjas} had suddenly appeared.

And their tactics were more annoying than she could ever have imagined.

All sorts of ropes were strung up along the path, preventing fast movement.

But that didn't mean she could perform the state-of-the-art Movement Technique, Tactical Night Footwork\footnote{walking sideways like a military team operation}, so she had to just hold the Moonlight Sword (No. 6) upright in front of her.

However, the defense in her lower body was lacking.

"Ack."

A-Qings body was yanked forward by a thread that caught her ankle.

She became the very definition of a human cannonball, flying toward a tall tree she would soon crash into.

She pulled Changming close and hugged her tightly, trying to turn her body to protect her somehow.

And then, Bang.

The impact on her back knocked the wind out of her.

She forced air into her stiff lungs and checked the girl in her arms.

"Ughhh.. are your ears, nose, and mouth all still attached?"

"Eung."

"Your arms and legs too?"

"Eung."

"Well then, let's go. Fucking cowards. They don't fight fair and square."

A-Qing stood up, tucking Chen Changming under her arm. And then, she set her down again.

"I can't do this with only one arm."

A-Qing stripped off the upper part of her robes.

"Get on."

"...Why are you undressing?"

"Ahhhh. This is called a baby blanket. It's a proud Korean invention. Wait, is that right? Anyway."

A-Qing wrapped Chen Changming up tightly within it.

{\itshape Now, my era as a one-arm has ended!

I's all over, you fucking ninja bastards.}

A-Qing muttered coldly.

...But then, there was a pit.

A certain level of trust was needed when it came to footwork techniques.

It was the trust that, at the very least, the ground wouldn't betray you. After all, ever since humans began walking on two legs, the earth had always solidly supported people.

But the moment she forcefully stepped on the ground and it crumbled and sank beneath her, it was enough to shatter that fundamental trust.

The silver lining was that A-Qing was transporting cargo that could not die under any circumstances.

Otherwise, she would have already become a cold corpse lying among the bamboo spears and poisons at the bottom of the pit.

What greeted A-Qing instead was sticky, spurting red mud.

{\itshape What's this? Mud? Is it a red clay pack\footnote{traditional Korean skin care}?

Or did they make it just to piss me off?}

Overcoming a pit about half a meter deep wasn't difficult for a martial artist at the Peak Realm.

All she needed to do was jump out of it.

A-Qing thought to herself that they were bothering her with all sorts of trivial things, as she dashed away again. But when she did so, her body felt as if it was getting extremely weighed down.

\textit{Fuck, so that's why they put mud.}

Peep Peep-!

That damned whistle sounded again.

A-Qing turned her head.

Because of the gloomy day filled with dark clouds, the shadows of the forest were even denser. And under such a shade, she saw a figure in black quietly stepping back. 

It kept going like this.

They would slow her down and hide, then blow the whistle to reveal their position.

\textit{This motherfucker. Where do you think you're going?}

Ding-! The head of the person in black was split in the shape of a whirlpool. The rest of the body kneeled before collapsing chest-first into the ground.  

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The situation was getting worse and worse.

These black-clad bastards weren't ninjas.

They were different from the sons of bitches she had encountered so far.

Strictly speaking, they were hunters. That's right, hunters.

And not just any hunter. They were highly skilled professionals.

There wasn't a single place on her body that didn't hurt.

Surely, when she woke up, her whole body would practically be a festival of colorful bruises.

The cuts from the sparse spring branches stung as mud got into them.

She had lost the Moonlight Sword (No. 6).

She ended up dropping because of the slippery mud on her hands, and before she could even retrieve it, a net was thrown onto her.

She blasted the bastards rushing at her with the Buddha's Palm and escaped while they were staggered, tearing through the net.

{\itshape It was an excellent sword that cost me half a sycee of gold, though.     

Goodbye, my Moonlight Sword.}

A-Qing mourned silently, inwardly shedding tears and singing farewells.

There was a hole in her thigh.

And when her ankle got caught, making her crash down, there was a sharp branch that just happened to stick out there.

It hurt terribly. It still hurts.

The pinky and ring finger of her left hand dangled limply.

She placed her hand wrong when she fell into the pit.

Of all things, there had to be a rock there.

She sighed deeply as she burst out, only to come face to face with one of the men clad in black.

Just like she did in Luoyang, she tore out his Adam's apple, drenching herself with blood. 

And then, when she did so, a single drop of moisture touched her cheek.

The sound of the forests rain announced its arrival.

Pitter-patter.

The sound of rain hitting the leaves gradually intensified.

And then, Rush Roar-!

The sound of frying oil filled the entire world.

\textit{It's even raining now? I'm gonna lose my mind.}

A-Qing sighed deeply.

And then, suddenly, an idea occurred to her.
