\chapter{A sad legend, what kind of legend was it? (8)}

Jang Su-hwa looks betrayed.

"You said you would save me……"

"No, just ask."

Jang Su-hwa's eyes are rolling and rolling.

Because that's what they usually say when they're biting each other.

It's okay, tell me, I don't have any lingering feelings?

Hmm. I see.

But why did you do that? Don't you know it's wrong?

No, I'm just asking.

Why did you do it when you knew it was wrong?

"I just took orders…"

"Ah. Order. Order was good."

Qing was giggling.

If you receive an order, can you just kill someone?

So who should pay the price for the evil deeds committed by the order?

The guy who gave the order?

So, if we just get rid of the guy who gave the order, then the group was not at fault?

So, what do the members of the group do?

Enjoy the good things and avoid the responsibilities?

It's a really difficult problem.

But in times like these, wouldn't the evil karma be glaringly obvious?

The red numbers are encouraging him to kill this bastard.

"Well, then, I will now……"

"Okay. A promise was a promise."

After Qing puts away his sword, Jang Su-hwa finally lets go of his neck and lets out a sigh of relief.

I couldn't breathe because my hand was pulled away, but there was a hole in my throat.

And then, Qing Qing lifts his sword and points at the rippling riverbed over there.

From Qing's perspective, he was a nameless punk and a pervert.

"Oh, but do you see that guy over there? Is he dead or alive? Anyway, if he's not dead, he's alive, right?"

"……!"

Jang Su-hwa tries to shout urgently, but seems to have forgotten to cover her throat before speaking.

Qing shows off his white teeth.

It was a neat set of teeth with prominent canines.

The ratio of female soldiers to male soldiers in the political faction was roughly three to one to four to one.

Ximen Surin was furious about this.

When recruiting new disciples, they always select men, not women.

So, even if you say she was a female warrior, most of the time she was the daughter of a warrior and learned martial arts naturally from a young age.

Since women are not chosen even if they are talented, isn't the martial arts world being controlled by men?

So the responsibility of a disciple was very important.

The future of all female martial artists in the martial arts world rests with the disciples.

If my disciple becomes the best in the world and makes a good name for himself, the world of martial arts will no longer be able to look down on women!

But it doesn't sound very convincing to Qing.

Hmm, Master. That's a bit much.

It's not that we don't hire women, it's that women don't apply.

It's not like they just drag a log and count the number of push-ups they do. It's like all the elders are mobilized to look at the talent, evaluate their bones, and gauge their tenacity. What sect would choose a man and not a woman?

However, this does not mean that Qing should refute Master's theory of a world for women, by women, and for women.

Even if the basis was a leap, distortion, and incitement, the conclusion was ultimately correct.

If the best in the world were a woman, the number of women interested in martial arts would increase significantly.

The process was whatever, so as long as the answer was correct, isn't that all that matters?

The statistics on the ratio of female warriors in the sect are even more dire in the case of the Sapa.

At least the political faction was three to four against one, what about the four factions?

Female warriors are rare in Sapa.

First of all, the atmosphere of Sapa was like that.

Sapa was a person who regards his younger brother as a convenient servant, a slave, or a plaything to pass the time.

If you have a brain, you can figure out what kind of dirty things you'll see if you go in there.

So what happens when a bunch of bad boys raid a town?

The man dies and the woman follows soon after, though she outlives him.

"We didn't kill them all. We don't just go around killing people, we just cut down the ones who resisted and store the rest in a warehouse, or rather, we keep them."

How many times has Qing seen such a dirty sight?

Those who rebel are the ones who get cut down and left behind.

Calling that an excuse, you are in a hurry and your true feelings are clearly revealed.

Men are cut down and women are, well, they are the ones who kill.

But I'm still tongue-tied.

Qing reflected.

I don't regret the act of biting my tongue.

Rather, the process and method were wrong.

The tongue should have been cut with a knife.

I regret having crushed it with my hands.

The eyes of Qing, who reflects on his own actions, are as blue as the sky after a typhoon has passed.

At some point, I started to feel a sense of rejection towards the thrilling pleasure that comes from killing evil people.

That was also the reason why Qing's methods became increasingly simpler.

I couldn't enjoy it like before, taking my time and slowly picking out each piece, thinking, "Wow, I've met the one to kill."

Just squeeze it hard and crush it, or take out the bones and throw them away.

There was no substitute for crushing bones.

If you just break it, you can always put it back together later, but if you want to leave him permanently disabled, you have to crush the bone so that it can't be put back together.

But they are people for whom a comfortable death was too luxurious to be killed with a single stroke.

So, Qing's method becomes simpler.

Or indirectly harming them, such as by burning their blankets.

This was a healthy example of a pleasure killer restraining himself from pleasure.

But just now I couldn't stand it.

Now that I know that if you poke a hole in my throat you can close it, I'll have to cut off my tongue to close my mouth.

The tongue that was caught by forcibly opening the jaw.

The feeling of crushing a slippery but firm lump of muscle, the jaw desperately closing, the teeth pressing down on the skin… … .

How can a beautiful demonic hand of a minority demonic master be called one of the ten greatest demonic masters in the world when it's barely damaged by teeth?

How long has it been since I've had a proper meal?

And when I came to, I was holding my tongue in my hand with the root still attached.

Because I pulled out the first one of the Saphanoms lying on the floor alive.

So, Qing couldn't help but regret it.

I should have just cut it cleanly with a knife.

But, I really couldn't stand it.

That crunchy, tingly sensation of the flesh being torn off.

Miss, this was really going to be crazy.

But still, it was a great success… … .

But Qing's few good qualities, his easygoing nature that allows him to quickly shake off past events, soon shine through.

But why was my body so flabby?

I feel tired even though I haven't done anything.

Anyway, there aren't many of them in the village, right?

In Gangpaecheon, a considerable amount of investment was made to acquire the absorption magic.

First class, no, what was first class?

There are eleven of them in the first generation, twenty-one in the second generation, thirty-seven in the third generation. There are three elders.

There's even a guy named Socheonju Kang Sakmun there.

They say that Gangpaecheon was not the lord of the universe, but the lord of heaven, and that his son, the successor, was called the lord of the small universe.

Thanks to this, I also gained the useless knowledge that the river in Gangpaecheon was called a river because it was named after the Munju surname.

But Kang Sak-moon was said to have set up a luxurious residence in the village chief's house and then just played around and fell asleep.

It was truly a behavior befitting of a successor to Sapa.

Only those who live in luxury and command their younger siblings with their fingers are worthy of being the master of the Sapa.

Anyway, now that the Socheonju has firmly established himself, even a fart-blowing guy from Gangpaecheon can't afford to be lazy.

Everyone climbed the mountain to find the Shingamyo, so the only ones left in the village were Kang Sakmun and his two great disciples, his right and left arms.

And the six disciples of the second generation who hold the line and defend the stronghold while others climb the mountain, or to be exact, lie down and suck up honey.

Of course, they would laugh and protest, saying they have no idea how difficult it's to work three shifts.

There were six, but now there are four.

Who are the three great disciples?

Where did you get lost? You have to go up the mountain right now and find the emergency supplies or at least the spirit.

Three generations dare to mention the defense of a stronghold?

Let's gather together under me and above you?

One for Unrestrained Realm, one for Super Climax, three for Climax, and the rest are first-class. There's no need to count the numbers for first-class, right?

Even the so-called successor was only the peak, and the ultimate peak was his right arm.

The blue calculation was correct.

I guess I can just clean it up quickly.

What about Unrestrained Realm? The Master will already be inside.

If you are a master in the midst of extreme (omitted) extreme training, what kind of opponent would a single Buddhist scripture be?

That was when.

"Hey! Who are you!"

A loud voice filled with inner strength.

The sound of weapons clashing fiercely was not an ordinary one, but rather a powerful one.

Qing immediately realized the situation.

Clash of the masters of Unrestrained Realm!

Qing jumps over the wall in one step.

Chen Changming and Murong Ju-hee are lying face down under the bushes to the west, waiting for the signal.

Because I told them to jump over the wall together if there was any commotion.

But when did that noise come about?

Chen Changming thought.

I'm so awkward. When was my sister coming?

Mo Yong-ju thought about it too.

This was so awkward, man.

The old Murong Zhuxi would have done the same.

There were many women who wanted to become friends with Geomhwa, and he was always the one who spoke to her first and tried to please her, so if she was a woman with big breasts, he would scold her, but if not, he would feel happy to see her in the same situation.

But now, Murong Zhuxi was no longer the reckless and strange woman she was back then.

I apologize to each and every member of the Phoenix Society for being so rude to them.

Because I was the first to reach out to outcasts who didn't fit in.

Thanks to this, the general atmosphere at the Phoenix Society was that people had suddenly become human.

Now that Chen Sui was out of the office, there are rumors that he was doing some proper political work.

But Murong Juhee didn't care.

It's all karma, you say.

So now, Murong Juhee doesn't hesitate to speak first.

"Hey, did you say Changming?"

"Unyeon. He told me to use a pseudonym for small talk."

"Yeah. That, Ximen, no, Unyeonyeong, um."

Mo Yong-ju-hee couldn't bring herself to continue speaking.

A pseudonym was a pseudonym, but if you use the name of someone you know, wouldn't it be a traitorous bitch who's attached to the blood sect?

Even if it's a pseudonym, it's not possible to call her that, so Mo Yong-ju-hee changes her title.

"You said he was your younger sister."

"What's wrong with you, young lady? You're weird."

The little one was being rude.

But this was the true nature of JinChangming.

Wasn't there a precedent in Qingdo where you gave someone food and then got scolded?

A slight tendon bulges out from Murong Zhuxi's forehead.

"You saved me before, young lady. Actually, I'm even more grateful for what happened after that. That's why I decided to call you young lady."

"Still, it's strange."

"What? We call Confucius ‘Mr. Confucius,' but why can't we call a young lady ‘Mr. Young Lady?'"

"uh?"

What about Chen Changming? Does that make sense?

"How was your majesty usually? I'm sure you devote yourself to training all day long. So, even for a woman, you've reached the peak of your powers at the youngest age."

"uh."

"Has anything happened?"

"doesn't exist."

"What kind of person was your godmother?"

"I don't know either."

If the other person was not willing to talk, talking first will not lead to a successful conversation.

This little kid… …!

Murong Zhuxi also doesn't particularly regret her friendship with Chen Changming.

So just keep your mouth shut.

"Ouch, my back. This was much more uncomfortable than I thought. Your Majesty, you must have had a hard time."

Yes, fake breasts are extremely uncomfortable.

First of all, since Mo Yong-ju-hee treats it like such a precious treasure, she has to lie face down and bend her back as hard as she can and support her weight with her forearms in case it gets pressed or bursts if it gets pressed.

Not only that, it was heavier than I thought, and the back of my neck where the strap was attached felt stiff and painful.

And the material feels sticky and doesn't breathe at all.

Even though I only had it for half a day, I had the unpleasant experience of sweat dripping down my chest.

But the metaphor was much heavier than the reality.

Chen Changming's ears perked up.

"Are you uncomfortable? Are you having a hard time?"

"It feels good to be here, but it's not real anyway. It's definitely heavy, and the swaying weight adds even more weight. I can't even see my feet. I have to step on the stepping stone, but how does your majesty fly like that?"

The fact that you can't see under your feet was also a very fatal weakness.

Ordinary drones step on the law and check the ground beneath their feet at every moment to determine if there was any danger.

It was disconcerting because you can't see anything even if you look down every moment.

Of course, this was a weakness that people who are born tall are unaware of because they have never seen the bottom of their feet.

Because a person born with three eyes will see things differently than a person with two eyes.

"Huh. I still want to grow up."

"Yeah. Me too. I trained hard because I knew I'd grow bigger when I reached my peak."

Chen Changming's eyes widen at that.

"Really? Does it get bigger when you reach climax? Yours was still the same."

"I believe so. They say that a complete transformation was made up of the most ideal body. So, if I dream, if I dream of an ideal body, wouldn't I be able to achieve it?"

"Oh. How? How do I do this?"

Chen Changming's eyes are bright and sparkling.

And in those eyes, Murong Juhee read a desperate pain that was very familiar, and therefore understandable.

And Chen Changming also noticed the pain in the eyes that were looking into me.

Oh, you too?

Yeah, me too.