\chapter{A sad legend, what kind of legend was it? (2)}

"There are many techniques for disguise, but the most important one was not changing your face."

"Huh? Then?"

"It's about changing characteristics. They say a person's impression was determined the moment you see them. Actually, I learned that myself, but that guy was quite famous for his physiognomy while working as a shaman, so I guess it's believable."

When I say that, I mean the previous Divine Thief sword.

In fact, the original relationship between the priests and priestesses of Divine Thief was already in shambles after completing the training of the Yuryuyeonryeon, and the chain of hatred and resentment could not be broken.

So, Tian Yuxue finds traveling with his disciples very enjoyable and enjoyable.

Wasn't he a good disciple who wagged his tail after enduring such cruel torture?

Of course, there was the bloody dedication of an old, evil soul, but since Qing didn't recognize him anyway, and no one in this world recognized him, he was truly an unsung hero.

"Oh. Features. What are the features?"

"I'm talking about the part that immediately catches the eye. Since you've always covered your face, if you just cover up your chest as much as possible, that's makeup."

His expression was sour.

"It's so frustrating and unsettling. I really need to feel my heart out…"

"It's actually good. That's why I'm interested in you as my disciple."

"Huh? Master? You were looking at me like that—"

"Hey, don't even joke around. It's actually easy for someone with such distinct features like you to disguise themselves. Disguises are easy for both handsome and pretty girls. And since you're so famous for your beauty, if you just cover up your chest, anyone can recognize you, and even if you just do a little bit of face work, you'll become a completely different person."

When Tian Yuxue evaluated Qing, he said that his incredible lightness was lightness, and that he was truly a genius of makeup given by heaven.

Look at that thing without breaking a sweat.

Once you put makeup on your face, you won't have to worry about it coming off.

If only he had been of average height, he wouldn't have been caught even though he had dozens of social statuses. It's a real flaw.

"In fact, if you just hide your chest, change your hair, and change your makeup, you won't be recognized by many people. Add glasses to that, and you'll be like, "Hmm, let's give it a try."

So, as Qing instructed, I painted my eyebrows very thickly, and painted my lips bright red, making them appear thicker on the outside.

"Changming'er? Number thirty-one."

"Yeah. Thirty-one times."

The two of them split their hair in half and began to twist it vigorously, then divided it into four sections and rolled them into circles, one on each side of the head.

By covering the head with silk and tying a pretty knot with a belt, the dumpling hairstyle most favored by the parents of young girls in Zhongyuan was completed.

It was cool in the summer because you can tie your hair up, and it's convenient for parents because they don't have to style it day and night and their hair won't get dirty.

Qing puts Tian Yuxue's disguise there.

"Changming'er? How are you?"

"Oh. I don't recognize you. And you seem really smart."

"It's not that he looks smart, it's that he's smart. Look, Confucius said, "He who knows cannot overcome him who loves, and he who loves cannot overcome him who enjoys."

A supporter was not as good as a supporter, a supporter was not as good as a supporter.

In fact, it was a word that Qingdo knew before it was released.

It was truly unimaginable that those were the words of Confucius.

"Wow. That's clever. Do more. Do more."

But Tian Yuxue looked at his disciple with an expression that said he was embarrassed.

"Confucius said, 'Don't associate with those less powerful than yourself.' Hmm? How can this be? What's going to happen to Changming? If Confucius says so, then Changming shouldn't even talk to me, right?"

Reporter Moo-Bul-Yeo.

Don't take as a friend someone who was worse than you.

The tendons on Tian Yuxue's forehead are prominent.

Then he threw the pig's trowel he was holding and it hit Qing in the face.

Chen Changming's somewhat savage expression was a bonus.

"Here it's. The reporter Mu-u-bul-yeog-i isn't saying you shouldn't associate with worthless people. He's saying there are no friends in the world less worthy than yourself. Confucius, who said everyone you meet on the street was a teacher and from whom you can learn, would have ever distinguished worthless people? Who would have offered such an outdated interpretation?"

"Oh. Wasn't that what Haksa Oh of Yeongcheon said?"

"This kid. What the hell was that guy in third place talking about? He said he was third in the back, so all the other students were friends with him, except for two. That's why poorly educated people go around talking nonsense."

Blue may be aggrieved.

Because no one but Confucius himself could know what Confucius meant by what he said.

Because the writing of Zhongyuan was undeveloped, the interpretation differed depending on the reader.

What Tian Yuxue says was only the most moderate interpretation among them.

There was also a different interpretation of 'yeo', meaning that since there was no other friend among you, you should not be partial and take sides.

Some people interpret that the inferior part of someone who was inferior to me was not their knowledge or wealth, but rather their virtue.

Then the interpretation becomes like this.

Don't associate with wicked people or evildoers.

If Qing had known, he could have clearly refuted this by saying that no single interpretation can be correct.

But Qing doesn't know. How could he know?

So, unfortunately, Qing's claim that he was smart can be ruled invalid because there was no basis for it.

Anyway, since it was a top-class room, Qing said after examining the mercury mirror nailed tightly to the wall (it's common practice in all countries to secure expensive items to prevent them from being stolen).

"Wow, was this me?"

Tian Yuxue smiled happily at the rather enthusiastic response.

In fact, Qing didn't really think much of it and just wanted to say it once.

Even if it wasn't a disguise, the beauty beyond the mercury mirror was always unfamiliar to me.

I don't know if mirrors are common, but it's not easy to see your reflection in Zhongyuan, so I only see it occasionally and never get used to it.

Anyway, it's strange that instead of the usual beauty, a completely unfamiliar, intelligent beauty with an IQ of over 300 just by looking at her appearance has taken her place.

However, it's a bit of a leaky blue.

Because this wasn't the disguise I had in mind.

Of course, Qing doesn't hold back his words.

"But was that all? Don't you just stick something on your face, make a fake face, and turn yourself inside out and do things like that?"

"You know what? Simple and straightforward methods are always the best. Do you think putting something on your face will last three or four days? If it's oily, it'll fall off in less than two hours. But if you use something harsh, it won't come off at all. It's just a pain, and your skin will fill with heat, bruise, burst, swell, and fill with pus. It's a real pain, you know."

Here, the expression "filled with pus" does not refer to a serious illness, but to acne or pimples, as they are called in the Qing's hometown.

"What about that, Inpimyeongu?"

"If you put something over your face, does it sting or not? Of course, there are some things that don't, but they're expensive, and you can't get them just because you have gold or silver. Above all, they're awfully uncomfortable to wear. It's okay because it keeps you warm when it's cold, but do you know how sweaty it's at a time like this? The sweat just builds up under my chin and stretches like a bubble. Ugh."

"That! That! That's what it feels like when I wrap my chest. Do you understand how I feel now? You know that sticky, slippery feeling when skin touches skin? When I lift my chest, sweat drips down from underneath. That feeling—"

"You, Master, I have something else to tell you. What are you talking about?"

"You have to try it yourself to know."

"Huh. Where would I have to feel sorry for myself?"

You don't know that?

Does anyone know how to run with a racing heart?

Your life will change in an instant.

I get tired of touching my own things after just a day or two and I don't feel anything. Well, I guess I'll have to touch other people's things instead of my own so I don't get tired of them and I'm confident I can live with them for the rest of my life.

Hmm.

The sinister gaze of Qing turned to Chen Changming's chest, but soon the corners of his eyebrows drooped and he was filled with a sense of emptiness and disappointment.

Yi-mei, I should have brought Yi-mei… … .

That guy Hwiyoung, he said he didn't even know how to properly use the martial arts he had learned, so I left him here to teach him.

I searched to see if it was a strange martial art, but it didn't come up.

So I asked if that was right, if it was really the right thing to do?

He said that it was the best of the best, but the only drawback was that it wasn't completed yet.

He also roughly understood what I was saying.

If it's not a completed martial art, it might not work, you know.

Even though it's unfinished, if Yi-mei can reach the peak of her power, she can be called the greatest of the great.

I guess it's impossible for me to master it.

I want to flutter, flutter, flutter.

Jangmyeong, well, Jangmyeong was still a baby.

Why are you still here? Is that weird?

How long are you going to keep having children?

Chen Changming glances down at him, following Qing's gaze, a pitiful gaze that seems to see something very pitiful, and the tendons on his forehead flare up.

"What does this look mean?"

"Okay, stop playing around. If you kill your features and add new ones, no one will recognize you even after they've become familiar with you. Qing, you just need to twist your nose a little."

So, Tian Yuxue passes on the dough of the Divine Thief vision and adds it to Qing's sharp nose to create a shape that tilts to the left.

Chen Changming was given the precious opportunity to learn such an amazing technique.

But I'm not really interested because I'm indifferent.

He just clung to Qing's side, feeling the cool breeze from Hansimgong, and exuding a look of boredom.

Qing examines the mercury mirror again.

Just by slightly bending the bridge of the nose, the impression completely changes and one looks like a different person.

"If this was the case, every time someone sees you, they'll sigh, "Oh my, if only your nose was normal, you'd be a perfect beauty. What a shame, such a shame." That's what I mean by "impression."

People don't remember faces by drawing a clear portrait in their heads, but rather by imprinting these features onto themselves and then combining them to recall them.

"Then what about Jang Myeong?"

"First, we need to create a characteristic. Do you know where a man immediately looks when he sees a woman?"

"My heart."

"Hmm. Is it possible to guess by asking?"

"You think I wouldn't know that? I even cover my face when I go around, so I don't even look at anyone else? Well, I understand, though."

"Men are born that way, so don't be too offended. Anyway, when a woman puts on makeup, it's advantageous to have a body type like yours that's either large enough to be wrapped up and hidden, or one that doesn't have a fetus at all and can be filled in."

Chen Changming's eyes take the shape of an axe blade.

Tian Yuxue just laughed and said, "Heng."

So the lecture continues.

How to make fake breasts that look amazing.

It's like a shower in a drought, like a healing water in the desert, when you already feel sad.

Qing's expression brightens.

"Wow, really? Is it really that good?"

"You'll be surprised when you see it too."

"Make it right now."

Tian Yuxue chuckled at Qing's reaction.

I heard that Divine Thief was one of the many methods used to seduce disciples, so I think this part will work well.

After seeing, hearing, and practicing the very systematic fake breast creation technique, Qing finally saw the result and couldn't help but exclaim in awe.

Wow, what was this? Is this a real chest?

The size, shape, and weight are perfect, but the texture was a bit sticky, which feels uncomfortable, and the center was just filled with a single hard bean.

Then, a thought suddenly occurs to me.

Isn't it strange?

Didn't you say I was the first female warrior?

But why did they put so much effort into making fake breasts?

The fake breasts of Zhongyuan are at best just a ball of cotton sewn together, but this was something that suddenly seems to have leaped over its time?

When Qing was curious, he cannot hold back.

"Is this also a family vision? Why on earth do you have such a vision? What purpose do you serve that requires such elaborate effort?"

Since he has a great reputation, he doesn't call himself a Divine Thief priest, and Tian Yuxue continues to be the family's vision.

"Huh? Of course, it's the chest that's involved. Hmm. Ahem."

Tian Yuxue answered in a puzzled voice as if asking why he was asking such an obvious question.

The girl acts like a total man, sometimes blinking, but she's still a woman.

Tian Yuxue recalled the previous Divine Thief.

-Hey, you smart disciple, you're all thick-headed but you're completely useless. Hurry up and try to learn the Four Stars of the Muyeong Shinsu, and your master will teach you something amazing.

-What was it?

-How to make a woman's breasts.

"Wow, that's amazing. Master, could you please teach me right now? I'm ready to listen right now."

"Ahem, well, when it comes to disguises, isn't the best way to hide your gender? Women don't get suspected even if they wear cotton, so if you just wrap yourself in this kind of clothing, wouldn't you look like a woman instead of a man?"

"For something like that, doesn't it seem incredibly real? Wow, it really is. Don't you think so, Jang Myeong-ah?"

"Yeah. It feels a little weird. But if you put something like clothes on it, oh. It really looks the same."

"It feels good, wouldn't it be okay if I put some powder on it? Oh, Jang Myeong-ah, daebak. Wow, wow. Wow, wow, a big feast."

"Yeah. Really."

Tian Yuxue was sweating profusely.

To be honest, it's a fake chest and a metaphor that has come this far through the intense obsession and improvement of past Divine Thief warriors.

However, it's a bit unfair that Tian Yuxue receives the same treatment.

He just had no interest in women by nature, and because of his circumstances, he wanted to wander the world rather than women.

Because he was from such a good family, he was a natural scholar who never regretted anything, even if he was attracted to women.

I made a metaphor and played with it several times, but I didn't really try to improve it.

But doesn't that sound like a very unconvincing excuse?

To be honest, I just told you exactly what I learned.

I made them a few times for fun when I was young, but I never bothered to make fake ones.

Of course, when the master was cleaning the bed, he would often appear with his chest covered.

Sometimes, if it bursts because I was rubbing it so much, I had to change the entire blanket and bed.

Well, if you were to rank the Master by character, nine out of ten would seem to have absolutely nothing to do with women.

When Tian Yuxue saw it, it was clear that the master had become a Taoist priest not because he was practicing the Tao but because he wanted to make up an excuse for not having a woman.

Anyway, I felt that Tian Yuxue was treated very unfairly and unreasonably, and I felt a sense of injustice and frustration.

How can you not say no to something that's not true?
