\chapter{A sad legend, what kind of legend was it? (14)}

The weather was really bad.

Even though the raindrops are quite heavy, what kind of wind was blowing like this?

According to the landlord, strong winds come with heavy rain once or twice every ten years.

I guess it's time to come this year.

As soon as Qing heard that, he thought, "Isn't that a typhoon?"

Is it okay to climb a mountain when a typhoon was blowing?

But Tian Yuxue was like, no matter how strong the wind and rain are, it's not like it's something a person should worry about.

I guess that's what I'm asking him to do.

However, even so, it's not a good weather to sit on the floor and watch the rain.

This was because when the wind blew violently, the raindrops would follow the flow.

If you don't want to add moisture to your skin, there's no reason to watch the rain on the veranda during a typhoon.

But Murong Juhee sat like that.

I sat there for a long time blocking the rain that had already poured down with my body, soaking wet, with raindrops dripping down my chin.

At that time, in the village warehouse.

The women were locked in a warehouse, or rather, they weren't even locked up.

The warehouse door wasn't even locked.

To be exact, there was no need to lock it.

When I opened the warehouse door, I was met with countless gazes, eyes that were already dead and hollow.

How many tears must I shed before the moisture in my eyes disappears?

Women who were as dried up as corpses.

Even when I tell him I came to rescue him, he just follows me without saying a word, so I get no response to the comforting words, "It's okay now, you held on well," and "You must have held on."

It was to the point where I thought there was no such thing as a zombie.

Then, in the center of the village, I came across the subdued Gangpaecheon warriors.

Emotions begin to well up in the women's empty eyes.

Hate. Pure hate.

It was the moment when the zombie transformed into a human.

At that moment, Murong-ju realized.

It was better to be filled with any emotion than to be empty and without anything.

Even if it's just a fresh hatred.

So, Murong Zhuxi took action.

It was something I did without even knowing it.

He trampled on the back of the hand of the warrior Kang Pae-cheon, who was already groaning with broken limbs.

The sensation of bones breaking, crushing, and crunching under the soles of my shoes was vivid.

And then the executions followed.

Slaughter would be a more accurate term than execution.

Only then did the women begin to cry.

Some cried quietly, some wailed so heartbreakingly that their intestines were torn apart, and some screamed like beasts.

They cried like that, tearing off the flesh of their enemies, taking out their internal organs, crushing them, breaking their bones, and hitting bricks.

And there were eyes glued to Murong Juhee.

I cannot understand the complex emotions swirling in her eyes, filled with joy, sorrow, contempt, sighs, and resentment.

But at least one thing was clear.

Those eyes sparkling with anticipation.

That desperate plea to show me the destruction and suffering of my enemy.

I don't know why I'm appealing instead of doing it myself.

Perhaps he was too tired to join in the frenzy, or perhaps he just preferred to quietly observe the event rather than get involved.

So, Murong Zhuxi did what he had to do.

They skinned the animal, cut open the muscles, pulled out the bones, and took out the internal organs.

The process of slaughter was so vivid that it's like a sharp knife, with all the nerves in the fingertips to avoid death.

Murong-ju looks down at her hand.

That was when.

"Hmm? Who's there?"

When Murong-ju turns her head, she sees Qing spraying water with her hand.

He was spraying water into the hand he had extended forward, and had the other hand behind him.

Whether it's a lantern or a torch, if you hold it out in front of you, it's so bright that you can't see your surroundings, so you block the light with one hand between yourself and your eyes.

Murong-ju bursts into laughter.

I've never heard of anyone using class as a light, and in fact, it's not like it's really that effective.

What a luxurious lamp this is.

Of course, it's possible to have superhuman vision.

"What's going on? It's pouring down rain. Oh my, I'm soaking wet. Why are you getting drenched in it? I'm going to get a cold at this rate."

"It's just cool."

"Is that right? If you're going to hit, hit everything. If you're going to say no, don't. It's not like I'm going to throw water at you in a disgusting way. Why?"

Qing answered as he sat down behind Murong Zhuxi.

"I have to hide behind the rain."

Murong-ju-hee smiles slightly at the warmth of my back.

If you don't like the rain, just go inside.

Why would you bother to come out and hide on the platform?

In the basement, I could now clearly understand what Qing was thinking at that time.

It was the greatest comfort that could be given to me.

Let go of all the pain, sadness, and hardship.

The events underground are brought back to life today through dismantling.

The pain expressed through trembling, the scream transmitted through the body with the mouth blocked, the hot drops of blood dripping down the face.

It's still so horrible that I'm shaking.

Even those women of the same sex are venting their pent-up anger as they seek revenge.

It must be a direct descendant of the Five Great Families.

All I can do was tremble at the mere dismantling of the villain, and vent my pain, sorrow, and fear to Lady Ximen.

"……Am I too weak?"

Murong-ju calmly pours out her heart.

Before we knew it, Murong Juhee's back was stiff and frozen.

"Hey, I wouldn't call you weak. Are you high on empathy? Do you have trouble seeing others in pain? Something like that."

"What was that?"

"But you did it anyway. Didn't you do something you didn't want to do just to relieve those women's resentment even a little? You wouldn't normally call someone like that weak, would you? Isn't doing something you don't want to do the real deal?"

"ah……"

Murong-ju's back becomes soft again, and she leans forward with all her weight.

Before you know it, you see Murong Juhee with a comfortable smile.

Yes, my most comfortable refuge in the world, the person I am always grateful for.

However, this time, Qing's return was confirmed.

What? After saying that, what?

So what I'm doing was a fake agreement?

Can someone who loves killing people so much that he only hunts villains be considered a true villain?

But I feel like Qingdo was wronged.

This was torture and murder, that's why.

How about changing it to interest?

Do you like being noticed too much?

If you're passionate about donating and volunteering just because you want to be noticed, and receive good attention.

And what if you're someone who feels joy in shouting out to the world that you're donating and volunteering and getting thousands of likes?

Even if you are the type of person who was interested, if you use donations and volunteer work as a means, aren't you ultimately a good person?

Or, even if we take an extreme hypothesis, perhaps he has a strange form of sexual attraction that makes him feel pleasure when he receives gratitude.

So what if you do good deeds to receive gratitude?

I'm just pursuing pleasure, but isn't it a good deed anyway?

But Qing was still frustrated.

Because these words only make sense if someone else says them. If I say them, it'll just be an excuse for my own rationalization.

But so what?

There's no one I can complain to.

I'm actually a pleasure killer who loves torturing people the most in the world, and whose heart pounds and feels electric when he hears their screams?

Even with the closest of friends, there are things that cannot be said, or rather, facts that should not be said.

There was a saying that if you are a true friend or family member, you should be able to open up to them.

This was just a nice-to-hear lie, a ridiculous piece of nonsense.

Some facts are meant to be kept to oneself and kept to oneself.

For you and me, for us, for each other.

Then, I start to feel a little annoyed.

What's wrong?

Even if he's a villain, was it too horrible to torture and kill someone so cruelly?

I like it, well, I like it, but I didn't know I would suddenly become a pleasure killer.

Then suddenly a thought occurs to me.

But was it right?

Actually, what if he was originally just like this?

If I had never killed anyone there, if I had never had to cut or torture anyone, then I would have just not known?

After thinking it over carefully, Qing came to a conclusion.

Wouldn't it be better if he was like this from the beginning?

What if he wasn't like this originally?

If this status window was polluting people's minds and such, then that's pretty horrible.

Besides, he doesn't really ask me to do anything.

It's not like they force you to die if you fail, they just leave you alone and say, "Do it or not, do whatever you want."

If I could control your mind, there would be no reason to leave you to do as you please, and I wouldn't let you harbor such insolent suspicions.

Was I a pleasure killer from birth?

It's a question that somehow makes me feel at ease.

If I was born like this, what's the big deal? Isn't it better to come to a better world?

It's a shame that I became a woman.

In a world where there are so many beauties.

Feeling regretful, Qing turns around and touches Murong Zhuxi's chest.

They're fake breasts anyway. I made them, so they're mine. They're something I can do whatever I want with.

Murong Juhee wasn't particularly flustered either.

Isn't it just heavy underwear worn under clothes?

"Hmm. As expected. No matter how well it's made, a fake was still a fake. It's a bit strange."

"Could it be because you know it's fake? I'm not sure."

"Is that so? Could that be so?"

Qing tilted her head.

Well, since Yi-meido and Gunyeongi have completely different feelings, if you think about it, someone in the world might feel this way too.

It may be that you feel a sense of discomfort because you know it's fake and think of it as fake.

But putting one bean at the end was a bit much.

Were beans the best option? Isn't there something else besides beans that's moderately firm, yet not too hard, and chewy?

Of course, Qing can't hold back when she's curious.

"Lady Murong. Is there anything we can put in the end here instead of beans? I don't know about other places, but this one was really good."

"Hmm. I also thought that part needed improvement. What do you think about cartilage?"

"Oh? Are you okay? But it'll rot quickly. I want the kind that won't spoil."

"then……"

The sound of pouring rain erases the sound of a friendly conversation.

The faces of Murong-ju-hee, who has a serious expression on her face, and Qing, who was just chatting and not thinking about anything, are covered by dark clouds and hidden in the pitch-black night.

The weather was bad, but it was a comfortable night.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

What may be a comfortable night for some may be a terrible night for others.

Somewhere in the mountains, under the ground, it was like that.

"Report flooded area!"

"There was flooding in the areas of Gap-i, Eul-yuk, Eul-gu, Byeong-sam, and Mu-i!"

"What about the damage?"

"The drop trap was flooded, so it's currently completely ineffective. However, if the water was pumped out, it won't be a problem…"

"Why did you stop talking? It doesn't matter, but what?"

"The venom nozzle was partially submerged."

The middle-aged man's expression suddenly turns sour.

"No way? No way, right?"

"That, sixteen venomous spears are filled with water……"

"What? Aren't you going to look straight ahead?"

"I can't guarantee the power of the poison traps in the Jeong area. The poison has already leaked out."

"Does that make sense? Some of the ships are flooded, so why are all the ships failing at once? Surely they were designed to share the venomous lance?"

"Well, there's nothing we can do about it. Venom isn't an easy substance to manage. If the venom lances were all separate, it would require a significant increase in management channels. And venom was incredibly expensive. If it gets clogged along the way and becomes useless, it's all thrown away. It's much more efficient to manage it in one place…"

"You idiots, what's so difficult about that? Why did you bury the poison lance underneath in the first place? Why was it filling with water?"

"They said that the upper rock was unstable, so we had to dig down…"

The middle-aged man thumps his chest.

"It was my mistake to trust you. You couldn't even come up with that simple plan, so I left it to you and now you're in for a real mess!"

His subordinate bows his head deeply.

But he just lowers his head, his expression full of anger.

Of course, it would be a really easy task for a middle-aged man, a civil engineering expert from Zhongyuan who was known as Guisan Manbak.

He was not just the best, but if you say that Guisanmanbak Rock Yong was a genius of civil engineering who has no equal in the world and must be in tune with all the times.

But if it were that easy, I would do it myself.

Why would you leave it to someone and then later make a fuss about why it wasn't done well?

Of course, the rock dragon was so frustrated and upset that he bursts out.

If I try to do all the design work from start to finish by myself, why would I have subordinates instead of just working alone?

I left the details to him, but he was completely clueless.

Of course, objectively speaking, the individuals in the Blood Cult's Blood Cult are all outstanding designers.

But to a true genius, they are still nothing more than a bunch of idiots.

"First, drain the water! Drain everything."

Then he draws lines on the complex drawings that fill the wall.

"Keep the drainage ditch like this."

The subordinate's eyes widen.

For drainage above ground, it was enough to just dig it so that it flowed from a high place to a low place, but underground facilities were not built so easily.

So, the lines that the rock-cutters draw so easily are actually the result that a civil engineering professional would have to rack his brain for dozens of days to come up with.

As expected, you are an old man.

This was the moment when disdain turns into respect.

But respect was respect, and the report that needs to be done was not over yet.

"That, that place……"

"why?"

"The poison was dissolved in the flooded water, so we wait until the water level rises further and then dilute it…"

"That's what I mean, fart!"

The rock dragon screams.

"You're sleepy now with the water filling up? Mobilize all the kids right now and drain the water first. Can't we just put on the gas mask and drain it? Huh!?"

The expression on his subordinate's face suddenly turned sour.

A gas mask was basically a thick, heavy, and stuffy leather suit that's made so that not even air can pass through.

Wear that and bail out water?

It keeps raining?

The subordinate's eyes went dark.