\chapter{A sad legend, what kind of legend was it? (11)}

In Qing's judgment, no matter how strong Elder Il is, he will be no match for Master if he attacks together.

However, we still need to make sure.

What if I get hurt or get torn somewhere?

It takes a long time to get better.

I was sick all this time.

It's not a pseudo-Western region, it's a pseudo-China.

If it had been a similar Western region, I would have been able to save myself a little less.

With just one treatment or spiritual prayer, detoxification, disinfection, removal of foreign substances, bones realigning themselves, nerves reattaching, sutures, and natural healing can all be achieved in one session.

But why isn't there anything like that in this pseudo-China where people fly around and sparkle?

Is Western medicine superior to Oriental medicine?

So, we need to make sure.

Qing was kneading grain flour with blood poison and thinking about it.

But, how should I feed this?

I'm not going to swallow this just because you threaten me with it.

If I were to call it loneliness, I think it would be less repulsive than extreme poisoning, but he was the most precious Sapha puppy in the world to me.

Aren't you guys that would rather have one thorn stuck in your finger than ten thousand lives?

First, let's hit the forehead hard and open the mouth, then try to push it in.

Or, if I put some medicine on it and make it scream, I can just throw it and put it in.

But? Oh?

However, it's extremely annoying.

If I know that someone was precious to me, then I know that other people are precious to someone else too.

But on the other hand, I am very happy.

Is there anyone more precious than life to the Sapa people?

So, what if I kill that person?

I can't make it more painful than my death.

Are the children of the wicked innocent?

No, I'm not innocent.

If my father and mother lived more comfortably and preciously than anyone else with the wealth and power they acquired through evil deeds, shouldn't they pay the price?

Wealth and power are natural rights that must be inherited, but you refuse to inherit sin?

If I were to see it slowly disintegrate before my eyes, would I reflect on my evil deeds even a little?

Qing's expression was unusual.

Kangpaecheon's one thousand-year-old, Elder Il, thought it was natural because it was the kind of evil expression a terrible witch of the Blood Cult would make.

And then that horrible witch comes running.

Gang, Ganggi and Ganggi clash.

In that moment, Elder Il realized that the witch of the Blood Cult was not as powerful as Unrestrained Realm.

But realizing it doesn't mean you'll suddenly feel as confident as before.

Not one-on-one, but two-on-one.

If you have to use your internal energy to trap the poison and push it out.

At that moment, a shadow appears behind Qing.

The dagger of the Thousand-Yu Scholar rushes forward, drawing a dazzling, yet round and complex curve.

In an instant, flames burst out from Elder Il's eyes!

The poison that was finally contained was now running rampant again.

But if the body was cut, was the poison a problem?

It's the complete opposite of what it was before.

Tian Yuxue kept swinging his dagger and pushing forward, but Elder Il was only busy repelling the strong attacks, and he kept taking steps backwards.

Tian Yuxue smiles without realizing it.

"Walking backwards? Are you human or a monster?"

In fact, Tian Yuxue was a person who was not lacking in the world in terms of being a nagging person.

Elder Il's expression becomes utterly rotten.

"You're so good at avoiding that. Aren't you ashamed of yourself, a novice? Have you grown old?"

"Yes, you, you said something like that."

"I don't understand what you're saying. If it were me, I'd rather bite my tongue and die than retreat so shamefully. I'd rather die than retreat from an enemy in my life."

It was a giant crane that was swimming and rolling around on the ground.

It was a disgrace beyond description, a disgrace so great that it could not even be described as a disgrace.

That's what a Confucian scholar says.

Elder Il's blood pressure suddenly soars.

This was in line with the idea that poison spreads more easily.

"Yes, you. How dare you."

"What's so good about having a disciple? When you get old, you live for just one disciple. My disciple came running to save his master, but where are all your disciples? Did they run away, abandoning their master, to live for themselves?"

There was not a single word that does not irritate me.

"Kwaaak! I'll kill you!"

A fire blazed in Elder Il's eyes!!!

But Tian Yuxue was calm.

Tian Yuxue achieved great success in the Awakening Divine Art.

And spatial perception, which reads the flow of air through the skin, gradually expands its scope through continued accumulation of experience.

So, I could tell that there was a disciple supporting me without having to see him with my own eyes.

But? This bitch? What now?

"Your Majesty! No! That's betrayal!"

The voice of the blue echoes.

At the same time, a flesh-colored pillar falls upon Elder Il.

Elder Il raises his sword without realizing it, then puts it away in a startled manner.

That was why Qing swung both of Young Master's arms while holding them.

The man's foot hit the elder's cheek.

"Ahhhh!!"

The young master screams like he's dying.

There was no need to explain who was more hurt since the nerves of the Unrestrained Realm master were kicked with the foot.

Of course, since he was a young master whose pelvis was on the verge of being shattered, his feet weren't the problem.

"You, you, you……!"

Elder Il was unable to continue speaking.

Tian Yuxue lowers his eyes.

Even though you are my disciple, please.

I'm so embarrassed I can't even show my face. Huh?

"Your Majesty! Your iron will to punish the wicked! I am truly impressed!"

The young master's foot, having made a large turn, aims at Elder Il once again.

Elder Il steps back and runs away.

"You, stop! Stop it!"

"Master! Stop it! Yes, what did you say?"

"Eww!!!"

"Yes? If that's what you wish, my lord, then I beg your pardon!"

Qing leans back on the young master.

He jumps up as if nothing happened, holding the sturdy man in his hand, and swings the young master with great force, throwing him vertically.

However, this was not an attack targeting anyone.

There was no one down there.

But there was a problem because there was no one.

Elder Il hurriedly lands, lands, and runs towards the landing point.

Elder Il, who was just barely able to reach it.

Elder Il receives the young master with his body.

What a tearful dedication!

Qing's expression suddenly turned sour.

The dedication was good, but the two's outfits are a bit much.

Wouldn't an old man with no pants and a completely naked young man be rolling around in each other's arms?

Then suddenly.

"uh?"

What if the young master and the elder were dressed in proper attire?

This scene must have seemed like a noble act of loyalty that could not be watched without tears.

However, because the skin tone was excessive, it ended up being a sight so ugly that it was impossible to look at with open eyes, let alone showing loyalty.

Why?

Is there such a difference when there was only one layer of clothing to cover the body?

The act of sacrificing one's life to save the lord's son and the successor of the Buddhist order was no different.

Why do I feel uncomfortable just because there are two naked men entangled together?

Because the viewer's mind was different?

Do people judge with their eyes and eat with their hearts?

So people wear clothes.

If you see a body that's shameful and sublime, you will feel reluctant, and if you see a body that's beautiful and graceful, you will become lustful and your mind will become clouded.

Suddenly, he lost his mind and watched the heated discussion between the priests (since an elder and a senior disciple are priests anyway).

Why was Tian Yuxue suddenly acting like this?

Well, I was trying to wake up my disciple, who didn't know the situation, thinking that the sight was too shocking.

What? All of a sudden? Here?

Qing absentmindedly raises his sword.

It was a look that looks at something new and unfamiliar.

Why do people pass by so casually when they see you, without paying any attention?

When I see someone with a sword, I feel ominous and repulsive, so I unconsciously look at their face to see if there was any evil in their eyes and try to check if their expression was sinister.

What about the sword in the scabbard, the sword in my hand, and the sword pointed at me?

The essence was just the same old thing?

Well, the mind of the one holding the sword was different.

Ah, I see. The premise was wrong.

Qing looks at Elder Il and the young master again.

The viewer's mind has not changed.

Are you rolling around without clothes?

Of course, the mind of the person rolling around was lewd, so wouldn't he have taken off his clothes?

The viewer's mind was drawn in that direction because he understands the other person's mind.

The mind of another person creates a phenomenon, and people come to understand it by seeing its appearance.

Then, when my mind creates a phenomenon, others will be able to see and understand my mind.

A person with a knife was a person, but because the person holding the knife has a vicious heart, others will be afraid of him.

A knife held by a person was still a knife, right?

Since the sword was not in the sheath but held in the hand, isn't the blade the one that hurts others?

A person with a knife was a person.

A sword held by a person was a sword.

If so, then even a person with a sword can become a sword.

That moment.

Qing disappears from Tian Yuxue's sight.

All that's visible was a single sword.

It was a blade in the shape of a human being.

Just a cold, ominous blade, as if it were about to cut down everything with murderous intent.

"Ah. So that's it."

Qing, who had returned to being human, nodded.

Why did I almost drown with a cramp all over my body while using a super-transcendent super-transcendent super-clear quirk that was not even a cat's eye?

Now I understand.

Because the scenery that Grandfather Mucheondaeje showed me was so beautiful.

The branch the child picked up seemed like the world's most precious sword to the child, and he must have been able to do anything with it in his hands.

So, it seems that the imitation was quite good, following the most beautiful scenery.

Wow, but just how strong was that old man, Grand Emperor Mucheon?

To cut down a black person.

So, if you erase the person from the person with the sword, what remains was just a vicious blade, a sword of murder itself that seeks to cut people down.

The higher you go, the more poignant the realm of the Great Emperor Mucheon becomes.

The ever-changing cartoon was so beautiful.

why?

Because that sword was not a tool for cutting people.

how?

Is it because the Great Emperor Mucheon was the greatest genius in history, who distorts and changes even the essence, and even defies reality?

Anyway, what, maybe I'll be able to do it later?

More importantly, there was something important going on right now.

This was not a time to be immersed in the afterglow of enlightenment, but rather something that needed to be done right away!

That's bragging!

I did it!

"Master! Look at this! It's the union of the divine swords!"

Then Qing picks up the sword and groans.

"Uh… why isn't it working? It worked before?"

"Of course, since I am your teacher."

There was no way I could erase myself and leave behind a murderous intent in my master's memory.

He was already a very affectionate disciple.

In fact, to be honest, Qing was a very rough and rude disciple who occasionally runs away from home.

Even so, why was it that Tian Yuxue was ruining all his pretty habits like a daughter-in-law?

But I know that feeling.

I'm raising a disciple with this taste. What should I do if I'm more excited?

If I can't bear the intention of killing my teacher, then why bother struggling with a knife?

"No, it worked just now. What was it? Hmm."

He was a very arrogant and fearsome Qing who wields a sword and causes chaos.

Like a puppy that needs to poop, very restless.

"Well, that's great, but……."

Tian Yuxue's expression was bitter.

That's amazing! It's also great!

But what did you see that made you realize it?

He committed an atrocity that even a great master would not commit, swinging a hostage as a weapon.

Why was it suddenly a new sword union when I didn't even swing a sword in the first place?

If it's the union of the mind and the body, then I don't know. No, what was the union of the mind and the body? It's the union of two people. It doesn't sound like something that only a lewd, perverted person would use.

At this point, it could be said that Qing was a plague itself, a living recipe for intelligence decline that affects not only himself but also those around him.

Anyway, they're not swinging swords, and all I can see are two hideous, flesh-colored guys rolling around.

Where on earth can I find enlightenment?

Then, a start.

Tian Yuxue came to his senses.

Is this what you mean when you have an enemy like this?

Surprisingly, it was the living intelligence that escaped from the decline itself.

When I turned my head, I saw Elder Il sitting cross-legged, busy expelling poison.

Since I was destined to die anyway if it didn't work out, it was a clever tactic that blatantly took advantage of an opening.

Qing also turned his head and looked at the sight.

And then the tendon on Qing's forehead flared.