\chapter{A sad legend, what kind of legend was it? (10)}

Even though his shin was broken and his shoulder was shattered, he was a tower guard who barely managed to keep his balance by striking the ground with his sword.

Qing was honestly impressed, and holds the wrist holding the sword with her chin.

From now on, this Sapha guy was my weapon.

It's something I can wield at will.

It was the moment when the secret of Qing, the ability to swing people around indiscriminately, was revealed to the world again.

Unlike before, it was a man-swinging that had become even more powerful through the Yongsan Banya Gyeong.

Chen Changming and Murong Ju-hee were strangely well-matched, so if you add one more monster with incredible strength to the mix, it would be a breeze to take down the rest.

"Ah. Let's not kill them, but just crush their limbs."

"Your Majesty? That."

Murong Juhee shuddered.

But Qing was firm.

"They don't even deserve to die in peace."

"Okay, okay, okay."

Mo Yong-ju's voice trembles faintly.

Qing, oh my.

"Would you please look for the warehouse building to the east? They say there are some surviving women there. Check on them and prepare to take them back to the village. Um, you can help me out, too."

"Yes." "Yeah."

The two little ones head east.

Qing looks down at the Gangpaecheon unmanned vehicles lying on the floor with a cold gaze.

Elder Kang Pae-cheon swings his long sword repeatedly.

Before the trajectory of the river could even subside, the next trajectory appeared, and then the next.

The great sword was one, but it swirls around fiercely, leaving behind afterimages like a net.

Tian Yuxue was busy retreating back.

However, the divine technique of Divine Thief does not go anywhere, and it's possible to narrowly avoid it by a paper-thin margin as if performing acrobatics, in the dozens.

In fact, Tian Yuxue was a person who was particularly weak in one-on-one battles.

This was because he was not a man but a thief, and also a great teacher of Confucianism, so he refrained from killing.

But Elder Il was a professional butcher whose entire life has been a series of murders.

The difference in skill between life and death was huge.

Even the compatibility was not good.

Tian Yuxue was good at wearing Divine Thief's weapons and exploiting weaknesses by taking advantage of any openings.

But unfortunately, he meets a master of incredible swordsmanship, and he was out of breath just trying to avoid the monsters and all.

But the reason he endured without a single scratch was because he was an opponent that Elder Il had never met before.

Since the joints are bent in the opposite direction and their limits are unknown, how can you avoid them by making movements that are logically impossible?

Moment, gap!

Elder Il's great sword cuts Tian Yuxue's neck.

The head disappears above the body.

But? It doesn't taste good?

Tian Yuxue can stick the back of the head to his back with his own power.

Extreme flexibility.

The oil-based training method was only capable of reaching ten stars when learned through experience, but if you continue to expand its range of motion over a long period of time, it can reach twelve stars.

The celestial body was capable of many creepy movements, such as crawling and jumping.

If Qing had seen it, he would have said, "Oh, that, if by any chance you can fold your body forward, um, no, that was the kind of skill that would have made him talk nonsense."

Tian Yuxue's lost head grows back.

The hair that was folded back was raised.

"You bastard! Are you human or a monster?"

"It's a monster! Are you surprised?"

"Noom!"

A flame bursts out from Elder Il's eyes.

Oh my, Tian Yuxue.

It wasn't a mirror, it was a mirror, a mine!

An ordinary warrior would show his weaknesses when provoked, but when Mine gets angry, he becomes intoxicated with murderous intent and becomes even more absorbed in his martial arts, becoming swayed by it.

That means it's getting stronger.

The path of Elder Il stretches in a straight line towards the lower abdomen of Tian Yuxue.

"omg."

Tian Yuxue stretches out both arms high and bends his waist with all his might.

You might wonder why you would raise your arms, but this way you can give your body a rebound and move faster.

The crescent moon was bent like a crescent moon.

A posture that's impossible without oil training.

However, in the realm of Unrestrained Realm and Ipma, the individual's will transcends the laws of the world.

This was called an idea.

The elder's sword, which had been piercing the air, suddenly stopped as if it were a lie, and he lay down horizontally.

And the sharp horizontal movement like a lie.

Tian Yuxue's knees are bent vertically.

A ship that barely passes over the ship, or rather, stops on the ship without passing over it.

The blade of the great sword swings vertically again.

Tian Yuxue pulls with all his might the two arms that are supporting the ground.

The body of Tian Yuxue, who continues to follow.

The elder's great sword cuts the hem of Tian Yuxue's trousers that spread out between his legs and splits the ground.

Only the groin seam was barely cut.

The moment when Tian Yuxue, who was almost destined to become an eunuch without being able to get married, gasps and breathes again.

Elder Il rushes forward with his sword still embedded in the ground.

The cold, strong energy connecting the elder and the earth rushed towards Tian Yuxue's legs at the same speed.

Tian Yuxue crawls away like a spider on two arms and two legs.

In an instant, Elder Il's arm swells.

A massive blow that turns the earth upside down and splits the world in two!

Tian Yuxue rolls backwards in a pitiful manner, barely escaping the destruction.

"You little rat!"

A sword that hits the ground with a loud thud.

Tian Yuxue doesn't even have the presence of mind to answer.

Rolling left, right, and backward, twisting my waist left and right, and flailing my arms and legs, I managed to avoid it without getting cut off, but-

Suddenly, a fierce smile appeared on Elder Il's lips.

Soaring murderous intent!

The moment when Tian Yuxue's heart suddenly sank-

"Elder! Run!"

A dark weapon flying towards the head of Elder Wyaeak with a sharp voice.

The secret plan that Elder Il had prepared was canceled before it was revealed to the world.

First, let's get rid of the memory.

Taking advantage of the gap, Tian Yuxue flips over twice and lands on the ground.

"What a bitch, you bitch!"

Elder Il, whose decisive move was interrupted, was about to shout, but suddenly opened his eyes wide and shouted with a different emotion.

Well, that's because Qing held out her hand so that the drooping young master could be seen clearly.

"Oh, hey. Don't move. Your balls are going to fly off. Huh? Should I just cut them off? Should I cut them into a star shape?"

"You b*tch! Can't you let go right now!"

"That's too much. I get it. Just let it go."

Qing lets go of the young master.

The young master, still reeling from the shock of the explosion, collapses to the floor.

The sole of Qing's foot hit the back of the young master's head.

"Can't you just get those dirty feet off of me right now!?"

"This was really too much. Okay, I'll clean up after you."

Then he cleared his throat and this time he picked up the Moonlight Sword.

"You bastard! Who dares point a knife at someone!"

"No, how far should I yield, no, fuck, no, Master, why was that old man taking off his pants? Is he a pervert?"

"When I went in there to catch that young master, he was already in that state."

"Huh. So, the two of you. A love that transcends status, age, and gender? Oh my, how could this be? Ugh."

They are saying that the two of them ate together.

There was a twinkle in the elder's eye.

But the vile Qing had already noticed Elder Il's helpless state.

If you were going to attack, you should have attacked a long time ago.

"Wow, what the heck. Fire was coming out of my eyes."

"That's because I'm a mine. I don't know how to control my emotions, so my internal energy takes shape and burns."

"It's a little cool. Can't you do a flower arrangement?"

"How can someone who was so mentally uncultivated that his inner energy leaks out when he gets angry reach the state of Unrestrained Realm?"

"Well, then—"

"Don't increase the dose any further. Mine has trouble controlling her emotions. She might actually rush in and demand to die with you."

Suddenly, the image of the Green Forest General Chaeju, who had caused the infinite human meteor explosion, came to Qing's mind.

Hmm, that's a bit.

Blue was strong, weak, weak, strong.

I speak slowly without further hesitation.

"Elder? Shall we resolve this through discussion?"

"Do you think you can dare to touch the Gangpaecheon River and get away with it?"

"No, was that by any chance a sect rule? Is that what you're supposed to say if someone starts a fight?"

"What-"

"Oh. I cancelled just now. Hehe. Let's talk it out without hurting each other's feelings."

Qing lifts the young master's hair and shakes it off.

Was it because of the scalp on the verge of tearing, or the excruciating pain of a properly cracked pelvis shaking?

Ugh, the young master comes to his senses.

"master!"

"This, this was a thousand wins……"

"You bitch, right now-"

"Stop. Elder? Don't you understand the situation? Would you like to see this? Twinkle twinkle."

Qing appears to be raising a strong spirit.

It's a show of force, asking if I, along with the Unrestrained Realm master, have the confidence to win.

Elder Il's expression hardens.

"What do you want?"

"First, could you please tell me your identity?"

"……What are you doing?"

"My name was Unyeonyeong. I am a blood relative."

Oh, my. It's the moan that the young master lets out.

I couldn't hear the previous self-introduction because I was fainting.

"Blood sect! Why was the Blood Sect interfering with the main event?"

"Heh, then, would you miss the opportunity to control and control the successor of Kang Pae-cheon? Well, my conditions are simple. Do you happen to know about the Bloodline? Well, would you like to have this?"

Qing searches through her bosom and takes out a small pill.

"You bitch, how dare you……"

"Isn't that a bad suggestion? There's no need to harm someone who's been fed up with loneliness. Rather, they'll probably support you. Why don't you aim for the world together with the Blood Cult?"

In fact, Qing didn't have much expectations.

As was always the case with the loyalty of the Sapa guys, isn't it true that first I live and then loyalty?

So, negotiations have broken down, and farewell, Young Master. It would be a shame to go alone, so I should send Elder along on his way as well.

"If I eat loneliness, to you, my lord…"

"Huh? Really? Are you really going to eat it? Why on earth would you, young master, want to eat so much loneliness—"

"Go! Could a witch of the Blood Cult understand what loyalty is, what human nature is? I owe my life to my brother-in-law. You are no different from my own son."

"One thousand wins……!"

"Your Majesty, I am truly sorry that things have turned out this way. I should have protected you."

"No, it's all my fault. Ugh, I'm so ashamed, I'm so ashamed."

"Haha, what a lovely sight of loyalty. To be swayed by such trivial emotions."

Qing was making such a mockery.

There was no particular reason.

Because somehow, I felt like that was the way it had to be.

Tian Yuxue thought about it.

Why does the picture look a bit like the disciple was the world's greatest horse?

"Okay. Take the medicine."

"You know you swallow without chewing, right?"

"Keep your promises."

"Well, really. Is it really necessary to harm someone who has been lonely?"

He flicks the pill at Qing.

The parabola continues to the elder, and he lets out an unpleasant groan, then gulps and swallows.

Qing was honestly a little impressed.

Is this the loyalty of Sapa?

Do the worm babies get along with each other?

"Okay. Is that enough? Let go of the young master."

"all right."

Qing puts the young master down quietly.

But he was a young master with dozens of cracks in his pelvis.

I tried to stand on my own two feet, but the weight shifted so much that I couldn't even scream and collapsed, my body shaking.

"Okay, Master. Shall we step aside now?"

Tian Yuxue casts a complex gaze at him.

Is this correct?

Where did this girl get her loneliness from?

And why are you so good at pretending to be a member of the Blood Cult?

But I think all disciples have their own thoughts.

Tian Yuxue and Qing slowly retreat.

Then, Elder Il rushes to the young master.

"Your Majesty, are you alright? Is your body okay?"

"His lower body. It looks like it's broken."

"Excuse me for a moment. Can you feel it? Do you know where I'm touching?"

"Right foot, heel."

"Fortunately, my nerves weren't hurt."

Elder Il carefully touches the young master's body here and there, as if he were handling a precious piece of porcelain.

He treats me very kindly, almost like his own child.

However, it was not a good appearance as the elder was missing his clothes and the young master was naked.

Then, it seems like he has a rough idea of ​​the young master's condition.

"Just hold on a moment. I'll bring you a stretcher. Ugh, ugh…."

Suddenly, Elder Il lets out a groan.

Tian Yuxue asks quietly.

"What? Did you burst out in solitude? No, where did solitude come from in the first place?"

"Hehe, loneliness? The elixir was just grain powder mixed with blood poison. It seems the poison was starting to take effect now-"

"Blood poison? Are you talking about the poison of the death sentence?"

"Oh! You know Sasa! Sasa, you know, really, um, really……"

Qing trailed off.

That old man, it's hard to explain.

"Do you like tea? Are you wrinkled?"

"What are you talking about?"

"Oh, this isn't the time. Master, we have to finish him off before he excretes the poison!"