\chapter{A sad legend, what kind of legend was it? (12)}

Elder Il's move was truly a game changer.

Geon-gon-il-cheok means throwing dice (cheok) with the sky and the earth at stake (geon-gon) and a single game (il).

The woman of the Blood Sect who fell into enlightenment in front of me was disgusting.

How could heaven do this to the wicked witch of the Blood Cult? It was a lamentable thing.

But on the other hand, isn't this an opportunity given by heaven?

If Qing knew, she would be shocked.

If the heavens look down, would they show favoritism to me or the Blood Cult or any other guy?

Rather, shouldn't Sapa be grateful to the Blood Cult?

Isn't it because the Blood Cult was such a bastard that the Sapha guys have a comparative advantage and are considered to be the better ones?

Like a mustachioed man who took all the sins of the Westerners and gave a free pass to those genocidal people.

Of course, the Westerners have something to say too.

How can it be the same crime to slaughter a white, flesh-colored 'human' and to hunt an animal whose skin color proves it to be a beast?

Anyway.

Even Elder Il doesn't intend to completely drive out the poison.

I was planning to just deal with him to the extent that he could endure it, and then run away with the young master.

How vicious was the poison? The poison spreads insidiously, and if you take your eyes off it for even a moment, it will wrap around your entire body like a snake.

So, we must put the poison aside and take the young master to a safe place.

However, Qing's enlightenment did not last long.

What was this?

Am I funny?

What are you doing sitting down instead of fighting?

Qing quietly, but now, as a reserve warrior, he flows quietly like water without a sound.

And so, a nuclear blast of rage, a majestic honey chestnut, slammed into Elder Il's crown!

"Cough."

Elder Il suddenly coughs up blood.

A huge shock, a splitting pain in the head as you carefully control your energy!

If Elder Il had been a proper master of the art of firefighting, he could have endured it.

A mine was a being that's originally swayed by martial arts and true energy.

So, in that moment, the blood and energy flow backwards and tears apart the blood vessels of its master.

"Ugh, ugh,"

The gamble of a lifetime was a huge failure.

Unfortunately, the dice roll was a complete failure.

Blood was spitting out of the mouth, blood was flowing from the nose, and bloody tears are streaming down the corners of the eyes.

Rather, Qing was embarrassed.

I just hit him once?

If I keep doing this, my energy will be drained and I'll pass out.

So Qing kicks urgently.

This was a Qing that has properly learned how to close the Dantian without putting a strain on the body.

When you learn the difficult things, the easy things become automatic.

An opponent who was already unable to resist due to the possession of a coin.

Now, it's possible to break the danjeon to the extent of putting a strain on the body with your feet.

The tips of Qing's toes dig deep into Elder Il's lower abdomen.

Almost to the point where the ball of the foot was completely buried.

A hole was made in Elder Il's danjeon.

The spirit that was running wild and harming the owner's body begins to escape through the hole.

It's a bit of a rough method, but the aftereffects are that you'll no longer be an unmanned island, but it's still a method to save someone who's dying from coin possession.

The momentum of the elder, whose energy has been drained, rapidly declines and wanes.

Then, the blood poison that had been struggling with the true energy unleashed its poison, saying, "Finally, freedom! I will conquer humanity!"

"Ugh, ugh."

Veins stand out all over Elder Il's body.

Dark blood vessels stand out clearly, making old skin appear colorless.

Then, it seemed as if the skin was dying and turning black, and then in an instant, dead blood started to ooze out.

The true value of the Sasaui's masterpiece was revealed.

Destroys blood vessels throughout the body!

Blood spurts from every pore, including the pores!

Only then does Qing smile with satisfaction.

Phew, the old man almost had it easy.

When the devil's possession reaches your head, you won't even know it hurts, your eyes will roll back and you will die peacefully.

That was when.

"Sister, sister!"

Chen Changming came running and was urgently looking for Qing.

"asleep!"

"Ugh, ugh,"

"Hehehe, hehehe……!"

When Qing returned holding the young master's hair, a bloody feast was already underway.

Strange women are beating up the Gangpaecheon warriors.

Qing throws Young Master aside and hurriedly covers Chen Changming's eyes.

"Oh no. It says it's not suitable for minors."

"I'm twenty years old."

Chen Changming grabs Qing's hand and whines.

But, it's impossible for a mere Chen Changming to overcome the strength of the world's strongest, most ignorant woman.

"Changming should only see good things."

Chen Changming stopped in his tracks.

Chen Changming, who had been standing there for a while, asks.

"Don't you want to stop?"

"Huh? Me? Why?"

Is it really necessary to stop women whose lives have suddenly been trampled upon from seeking revenge?

"but……."

"Revenge was for the living. That way, those people can live too. Yeah? But, what about you, Miss Mo?"

Chen Changming pointed his finger at him.

Murong Zhuxi was seen wielding a sword among the women.

The mixed appearance was very natural because the clothes are shabby.

"He did it. If there's anyone who wants revenge, they can do it. That's why those women are like that."

"Young Lady? Oh."

"Oh, my lady."

Murong Zhuxi, who discovered Qing, kicked the unmanned Jiang Peiqian sword that he was teaching and ran at a brisk pace.

"Uh. Uh. My lady?"

Murong Juhee was watching Qing's expression with a somewhat restless and anxious look in her eyes.

When Qingi looked at the Gangpaecheon warriors, they were no longer human, but rather more like lumps of meat.

As expected, since he's not a professional, he probably doesn't know that he has to put his life on hold to survive for a long time.

"Ah. I heard the story. While we're at it, let's add this guy too. He's the leader."

"Ah. Net!"

But the young master will have to suffer more.

But shouldn't the living come first?

I need to start from the inside out, because wanting to cause more pain was just my greed.

Murong Zhuxi was visibly relieved.

Even though I thought that if it was Qing, he would have done this, I was concerned that he had told me to spare him instead of killing him.

Murong Juhee receives the hair that Qing gives her.

And then he drags you to the scene of bloody revenge.

There was no need for Murong Zhuxi to say anything.

The woman, who recognized the master's face, rushed towards him with a scream mixed with half-crying and half-screaming, calling him an enemy and a bastard to kill.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At sunset, the warriors of Gangpaecheon, who had spent another fruitless day, returned to their shelter with their tired bodies.

After wandering around the mountains all day, I'm hungry, sweaty, and sticky.

So I need to go back quickly, eat something, get some water from the well, and then bring the girls I put in the warehouse and stretch my body out a bit.

It may not be rewarding, but it's a reward that you deserve to enjoy after a fulfilling day.

The first search party to always return was the one led by Oh Cheon-seung.

The leader was Cheon Seung-in, isn't he an elder?

Even if you come back early, there was no one to criticize you for coming back when you haven't lost yet.

However, the expression on Elder Oh's face as he came down the mountain was not very good.

"What? Why isn't there any smoke? Did these kids forget to cook again? Ugh."

How nice it would be if the kids who don't even ride the mountain, who ride the line between the master and the elder, at least got to eat on time.

But lazy, honey-sucking kids are more likely to just spread out and not do what they need to do rather than being satisfied with their situation.

Even dinner preparations have been delayed several times for that reason.

Elder Oh gritted his teeth, thinking that today he would have to discipline these kids really well.

Of course, those who should have received that harsh military training have already passed away.

It seems that he was able to avoid the military discipline training of Elder Oh, who was already dirty and had even dirtier hands.

So, the dead Kang Pae-cheon warriors should be grateful to the Qing.

How could Elder Oh, who was coming down the mountain, know that fact?

So I'm going to completely destroy it today.

Did you come down here and look like that?

What was this?

"Open the door!"

But there was no news at all, no response.

Elder Oh's face suddenly distorts.

"These kids are getting away with it. Yeah, they don't even have boundaries anymore, do they? No matter how much the young master says, 'Come on, come on.'"

Elder Oh leaps over the wall and strides briskly through the village with an angry gait.

The search team was still out there.

Well, it wasn't Cheon Seung-nim who opened the door.

"What are you doing? Aren't you going to open the door?"

The first-class unmanned person glares.

And the second-ranking warrior conveys that gaze to the one below him.

"Yes, yes."

The three-legged warrior climbs over the wall, half in sorrow and half in disgust.

When you're a first-level senior, you can easily jump over them in one step, but you insist on using your third-level juniors.

Of course, for the unmanned personnel of the first level, this was a matter of authority, not efficiency.

I'm your older brother, so why should I open the door for you guys?

If Qing heard that, he would click his tongue and ask why on earth that was so out of place, and why he had to be the older brother when he wouldn't even open the door for his younger siblings.

Two Samgyewi warriors lift one of them, and the other one hangs on to the wall and struggles to get over the wall.

The guy who fell over unlocked the door from the inside and opened it, and the only thing you can hear was this.

"I thought you'd stay up all night just to open one gate. Those pathetic little bastards. Tsk tsk."

Well, if you feel wronged, you should have done it to the first-class brother.

The crew entered the base so late, but why was it so quiet?

The time has passed when the voice of Oh Cheon-seung, who should have been roaring loudly like a lion, would have said, "What are you guys doing!"

Then I see a blood stain on the floor.

An ominous feeling suddenly crosses my mind.

Oh, no matter how much Cheonseung tried to manipulate it, he wouldn't have made a fuss so that the ground was soaked in blood.

and.

Elder Oh, who entered first, was seen standing in the distance.

You might wonder why a person would stand still without a purpose, but when you see the scene unfolding before your eyes, you can't help but do the same.

Several corpses hanging from a tree.

There was no corpse with all four limbs, as there was not a single intact part.

If only the limbs are missing, it's considered mild.

Not a single speck of skin remained.

The weak-stomached Gangpaecheon warriors pour out what was inside their Weak.

Who committed such a heinous act?

Well, there's no need to question that.

Large letters written in blood on the wall.

Blood Cult Advancement to the World

Somehow, the humid air seemed to have a thick, bloody smell, so the Gangpaecheon warriors could only watch helplessly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

What should we do with the women we rescued?

It's not something you can just leave them in silence and say, "I know it's hard, but I hope you overcome it," and end it there.

What if those Gangpaecheon guys try to find the missing women?

He must have been very angry after losing his successor, so how cruel would he be?

However, I cannot just leave the absorption magic alone and take care of the women.

The answer is, then why not just ask someone else?

Even if you just send it to the nearby Hanam land, there was Taecheong Sangbang.

I thought I should leave it to my grandfather.

So, Qing sent several letters.

However, I can't trust those magicians.

Qing doesn't trust the character of the magicians.

But I believe in the power of gold and silver.

If you arrive without any injuries, you will be rewarded with dozens of gold coins.

You can't shut all the women's mouths here, so please serve them as well as you can.

It would be much more beneficial for the coachman to arrive safely at Taecheongsangbang
