\chapter{A sad legend, what kind of legend was it? (3)}

So, Chen Changming proudly shows off her fake breasts as if to say, "What's wrong?"

Qing looked at her and said.

"There was a reason it had to be elaborate."

If you wear fake breasts as a disguise, you should definitely emphasize it.

Because I put it on to show off to others, if I don't emphasize it, I'll just look like a big woman wearing expensive clothes.

Big breasts ruin the look of clothes.

So, it's the name of the Chen Changming that was gathered and exposed to the goal.

Why did he suddenly become so proud and raise his shoulders? Even though he was wearing a fake outfit, he seemed to be oozing with confidence.

Qing, as if it were natural, reaches out and squeezes the fake breast.

Of course, since it was fake, Chen Changming was not surprised and instead looked at Qing with bright eyes.

"how was it?"

"Hmm. Something feels a bit strange…."

For a fake breast, it's quite strong. What do you call it? Is it definitely elastic? Or was it weighty? Is it too soft? Like a water balloon?

I can definitely feel that it's fake, whether I know it or not.

Would it have been better if I had touched it without knowing?

Is this the red pill?

Chen Changming seemed to feel a sense of discomfort as he stroked my chest and tilted his head slightly.

However, Chen Changming, who had grown from a baby to a big baby, looked very satisfied.

Tian Yuxue poured cold water on it.

"But didn't I tell you? The best makeup was one that changes gender."

----

A brother and sister are wandering around the market.

Their faces are so similar that anyone would think they are siblings.

In fact, the only similarity was the thick eyebrows that are painted in the same shape, but strangely enough, that alone gives the impression that they are very similar.

The only thing that's unique was that the older sister was tall and manly, while the younger sister was much shorter.

It's a made-up Qing and Chen Changming.

Qing-ya looks like a smart woman who will do great things in a big place.

Chen Changming was a rich young man, no doubt.

A young master with his hair braided into a single braid and a white belt hanging down like a man's, and wearing a hero's hat.

The chin was thickened to give it an angle, the forehead was raised by adding flesh, and then it was extended in a straight line to the tip of the nose.

And by putting a large scar on her cheek, she gives birth to a very innocent little boy with no trace of her mother.

But he has a very sullen expression.

Anyone who sees it will think that it's heartbreaking.

"Why are you so upset?"

"I don't know."

"Is that why you don't let me wear earrings? Well, then should we go look at earrings? Wouldn't it be better if we wore something unique?"

Chen Changming shakes his head at him.

"If you wear it while disguised as a man, you won't be able to wear it later. What if someone with a keen eye for detail comes along?"

"Hey, even if you have a good eye, would you notice something like that just by looking at the earrings?"

"I don't like it if it seems like it would be even the slightest bit dangerous."

"Hmm. Changming'er was quite wise…"

I'm saying that I don't like it if it seems like it would be even the slightest bit dangerous to Qing.

But Qing didn't quite understand.

Look at how much risk a little kid takes, he's so scared.

Words must be spoken accurately to be conveyed.

Tian Yuxue left the room, saying he would get a detailed map.

While doing so, I asked you two to reveal your faces and use pseudonyms to find out more about Mount Lao.

"Huh, where are you going to investigate? If you just go around asking around, will you find anything suspicious?"

"Wouldn't the hunters know? Ask around, starting with the herbalist."

Of course, I didn't really expect that Tian Yuxue, who said this, would ask for any specific information.

It's just a trick to make people know about your fake name in the city and make them wander off to the wrong place, even if it means incurring resentment.

It was said that Qing was quite impressed by him.

Wow, do you really need to be this smart to be a Divine Thief priest? Wouldn't it be okay for me to be the next Divine Thief priest? Wouldn't it be better to just pick up a smart kid and pass him on to the next generation?

Anyway.

The alias of Qing was the same as that of Jeongban.

So, Qing wanders around the herbal medicine shop.

"Welcome! Oh, sir. Is there something you're looking for?"

He wore nice clothes and, above all, put that expensive body on his crooked nose.

Because the aeche was made by carving glass or crystal, it's an extremely expensive and precious item.

Of course, it's not like the hometown of Qing, where the pieces are tailored to the eyesight, but rather the best ones made by craftsmen are selected and brought in.

Of course, it's a fake, so it's just flat-faced glass, but it's still expensive!

There was even a nobleman sitting next to him.

At the appearance of a customer who appears to be rich, the herbalist immediately runs out.

"I want to see the three."

"Ah, you came to see the ginseng! What kind of ginseng did you come to see? There's a decent supply of Goryeo ginseng from Dongi across the water right now."

"Um, not dried ginseng. Do you have any fresh ginseng? I've received some old ginseng, so I'll get some fresh ones."

"Oh, don't be ridiculous. The hunters can't enter the mountains right now, so the medicinal herbs from the old mountains have completely dried up."

"Then, there was no Poria or Sapju?"

"Yes, yes. We have some medicinal herbs, but you can't find any raw herbs anywhere right now."

"Tsk. What the hell was this? I came up from Namnyeong because I heard that Mount Lao ginseng was good."

Chen Changming speaks up as if to tell him not to worry.

"Hello! Sister, there's more than just this herbal medicine shop in Imok. Let's look for another place."

Hmm. Changming'er. Aren't you raising your voice too much?

It's a voice that's so contrived that anyone who hears it would be suspicious.

And what if I emphasize the name too unnaturally when I tell them to?

Although the blue one was a little bit prickly, the herbalist who heard it didn't really think much of it.

Anyway, I walked around the market, visiting herbal medicine shops, eating grilled meat skewers, fruit skewers, all kinds of bottles, rice cakes, and wow, fish cakes! Hmm? What was that? Are they really fish cakes?

You might be wondering what this means. Then what does fake fish cake mean?

However, the fish cake of Zhongyuan was a specialty of Hubei Province, home to the Shennyeongmun Gate, and was a very high-quality food with a history of over three thousand years.

This was a fish cake from Zhongyuan that's made by grinding freshwater fish flesh and pork, then steaming it with egg and starch.

It wasn't the taste that Qing had imagined.

Should I say it's too fancy?

Of course, it's very delicious.

But what about this fish cake sold at the market?

Somehow, the taste of home was coming back, ahh.

Yeah, sometimes you need that cheap taste.

Whether it's a herbal medicine shop or a research center, I need to eat some of this fish cake I miss right now.

"The soup was done, can you just give me twenty bowls worth of garnish?"

"Huh? Did you just say twenty?"

"Twenty. Here, take the money and give it to me quickly."

The face of the fish cake vendor who sells twenty pieces at a time brightens.

It would be nice if it were a curly fish cake, but unfortunately, the fish cakes in Jungwon are either boiled in the shape of tofu and thinly sliced, or boiled in bite-sized round shapes, so there's nothing we can do about it.

"Hey, sister? You're going to eat all of that, okay?"

"You try it too. It's absolutely delicious. It's delicious."

"this?"

Anyway, Qing, whose purpose had changed to exploring the market for snacks, suddenly became serious.

Eating Ximen Qing's true heart was a very rare spectacle in Zhongyuan, where there was a dearth of things to do, see, and enjoy.

Even in the hometown of Qing, it wasn't long ago that eating and drinking emerged as a full-fledged pastime, so isn't this a time-traveling experience?

Naturally, the footsteps of people passing by stop.

A beautiful woman with a bright and intelligent face was lining up bowls of fish cakes.

And then, wouldn't it be like stuffing your mouth with steaming hot fish cakes and munching on them until they are full?

And how a bystander calls a bystander.

What the heck, was there a fire at the fish cake shop?

I was wondering if this was a house that was really good at something, and then someone came over and said, "Wow, there's a woman who eats fish cakes so well! And she's pretty!"

Chen Changming seems uncomfortable with people's gaze.

He grabbed the sleeve of the blue shirt and pulled it hard.

It's a call to go quickly.

But Qing was unwavering.

If I miss this opportunity, when will I ever get to eat it again?

So the fish cakes are reduced at a rapid rate.

The onlookers who were watching the sight with wonder became more and more amazed.

Will the woman be able to eat all twenty bowls of fish cakes?

A bowl that's getting smaller and smaller.

Everyone in the room gulped without realizing it.

Since it's said that even a beautiful person looks blessed when eating well, I think I will have a bowl of fish cake.

And so, the moment I put the last one in my mouth, applause and cheers erupted from the audience.

Qing turns to the audience, raises both hands, and responds to their enthusiastic cheers with a shout of victory.

"It's me! It's me! It's me! It's me! It's me! It's me! It's me!"

Carnivore? A meat-crazy woman? Then why fish cakes?

Hey, you bastard, isn't fish meat? Fish meat was meat, after all.

That was the moment.

"Master! Ten more bowls here!"

A surprising declaration from a carnivore!

The surprised audience gasped.

After eating twenty bowls, ten more?

But the silence was short-lived, as the crowd erupts in excitement, shouting, "Wow!!!"

"Carnivore!" "Hello!" "Carnivore!"

Actually, there wasn't that much toppings in one bowl.

If we convert it to the specialized unit system used in the Ximen Qing, it would be something like this.

For Qing, it's not that difficult of a challenge to make 40 or 20 fish cakes.

It's just a bit watery…

Since there are so many people here, I should sell more names now.

It was when Qing was swallowing the fish cake with a gurgling sound.

"Hey, ma'am. Did you say "Unyeo-nyeong"? Instead of these cheap fish cakes, how about eating something real? Only by enjoying a proper banquet at a jjimuk noju can you truly say you've come to jjimuk, right?"

What was this?

When Qing turned his head, a man with a sword, or rather, a man and several men behind him, were smiling at Qing.

Of course, even the most famous and famous tea ceremony must be held in a specific location.

It's already a place full of people wandering around looking for treasure.

Even if you cover it up with makeup and your nose was crooked, the beauty of the most powerful beauty in the world cannot be hidden.

Seeing a beauty who looked so formidable without even a weapon, wouldn't it be strange if bugs didn't bite her?

Qing stared blankly at the young man who had barged into the middle of the event.

What was this?

He was quite handsome and would have made many women cry.

So, I guess he must have been confident enough to say it.

"Thank you for your kind words, but I'm starting to feel hungry."

"Oh, my lady. Don't be so expensive."

His eyebrows twitched.

What was this kid doing when we first meet?

I'll crush your heart.

In the Qing hometown style, the word 'nangja' was used only when there was 'something' between two people, more than friends but less than lovers.

Friends are just called "young lady." Lovers call each other by cringe-worthy nicknames, from "Gaga" to "All sorts of animals," so the term "young lady" was used just about everywhere.

"Thank you for your kind words, but how could I have followed a man from my maternal grandparents without knowing it? Please refrain from such reckless remarks."

"We don't know each other. That's too bad."

"So, you know each other? This was my first time meeting you."

"Oh, well. If you know each other's names and faces, aren't we acquaintances? I'm the great founder of Seoho Chiljeol. So, aren't we acquaintances now?"

Qing waited for a moment.

One. Two.

Although I can't hear them shouting loudly, perhaps because they're not particularly famous, I can hear them whispering softly to each other, such as Seoho Chilgyeon and Baljeongpa-ssi, thanks to Qing's supernatural hearing.

The nicknames of the Sapa guys are different from what they claim and what the world calls them.

Usually, one letter changes at the end, and the world usually calls them by derogatory terms such as devil, dog, pig, barbarian, slave, etc.

"I didn't really want to know. Would you please step aside now?"

"Oh, why are you acting like this? You're being so expensive. Why don't you just have one drink? Okay?"

"Drinking in broad daylight?"

"Then, wouldn't it be okay to drink until night?"

"I'm sorry, but I have some business to attend to. Well, that's all."

"Oh."

And then he reached out and grabbed Qing's wrist.

Qing-i cheered inwardly.

This kid touched me first.

So, when Qing tried to swing his arm to fix his messy hair, he hit him.

"stop!"

The gazes of Qing, the gaze of Chen Changming who was very displeased, the gazes of Seo Ho-chil-gyeon, and the gazes of the onlookers who were watching how things would turn out all converged on one another.

There was one unmanned person with his face covered.

Judging by the crossed swords on his back, he appears to be a martial artist who uses dual swords.

Then, Pounce let go of Qing's wrist and brought his hand to my waist.

Qing tilts her head.

It felt strangely familiar, and I thought I'd heard the voice somewhere before.