\chapter{A sad legend, what kind of legend was it? (6)}

The name of the small town along the northeastern coast, surrounding the northern part of Mount Lao, was Kimgachon.

Although it's located near the coast and a port, it's not particularly bustling because it's located near a major highway and has a bustling port called Jeomuk-hyeon.

However, it's a village that can only be considered a city, with guests trying to climb Cheonwonbong Peak, which was relatively easy compared to its height among the peaks of Mount Lao, and a white sand beach called Noinhae Beach.

Kim Jang-ga? Is that the Kim? It's across the river by boat, so maybe you don't know?

Of course, no one knows.

Originally, the road leading to Mount Lao Mountain would have been bustling with guides, porters, rickshaw pullers, and merchants.

However, the atmosphere of the city was gloomy, and on the road leading to Mount Lao, there were only a few peddlers standing at their stalls, not soliciting customers, but just looking around.

Just looking at this, you can see how much of a blunder the people trying to find the magician are committing.

"Should I eat breakfast now? Wouldn't it be better to eat at a restaurant and then go home?"

"What breakfast? No. Okay. Let's eat. Let's eat."

Tian Yuxue said that he would just do that as he saw Qing's expression suddenly turn sad.

You're saying that you're not going to run away from life just because you're eating breakfast?

A breakfast so simple and plain, that the owner of the restaurant came out and offered us a free glass of alcohol, saying it was brewed himself?

That was when.

"Oh my, there he was again."

A young man, perhaps the owner's son, frowns sharply.

When Qing turned his head, he saw someone wearing rags. What the heck, a rag was wearing rags.

His eyelids were so swollen and black from being hit so many times that it was hard to see in front of him, his cheeks were swollen as if they were going to burst, and his lips were already cracked and covered in scabs.

There, the hand was swollen and looks like the bone was broken.

A beggar wandering around an empty restaurant sees Qing's group and shouts urgently.

"Sir! Sir! Please, please help me!"

Since the mountaineer's attire had to be changed secretly in a deserted place, the group was still wearing their regular clothes.

There were four people, four swordsmen, and of course one person was holding two, but they looked like martial artists and immediately started looking for the swordsman.

"Hey, why do you keep doing this? Do you really want to die? Can't you just get out of here?"

Jeomsoi lights a twin flame and strides towards the rag man.

I feel like I'm being too rude to the already pitiful beggar.

Since Jeomsoi was a rare blue number, Qing watched for a while.

Are people who have accumulated good deeds truly good?

"Sir, thank you."

The magpie roughly covers the mouth of the rag-wearing beggar.

Not with a fist, but with a rice ball.

As the beggar chewed and swallowed his food, Jeomsoi sighed deeply.

"Hey, a living bastard should live. You got beaten up so bad last time. Are you okay?"

"But, those guys…!"

"If you die while asking for revenge, what kind of death was that? And what's more, you're from a famous sect? If the government can't do anything about it, who can?"

"But, those bastards, those bastards who will tear you to death, ugh, Hyeopsa! Hyeopsa, eup."

Another bite of rice ball.

Well, if you do good deeds, good karma accumulates.

Of course, if the number was blue, then he must be a good person.

Qing sighed deeply.

Good people do good things because they are good. Isn't that the logic of the level?

He looked around at the group.

One indifferent look.

There was a single gaze that asked if I was not going to help.

He was rolling his extra-large butt around as if he wanted to get up and leave at any moment, but he couldn't come forward and had one gaze that was cautiously looking around.

Hmm. Three to one.

But Tian Yuxue's expression was hurt.

He snorts and says, "Huh."

Master, this was democracy.

Minority opinions are of no use.

If you feel wronged, you need to incite them emotionally.

"Hey, Jeomsoi. What's going on?"

"Oh, sir. Don't mind this guy—"

"Please help me! If you just help me, I'll serve you for the rest of my life! Please, please…!"

"Hmm. Master, do you need a servant?"

"Huh. No problem."

"For now, um."

Qing looked around.

I came into an empty restaurant as a first-time customer and started eating, so I guess the owner even gave me some free drinks.

"So, what's going on?"

So the rag-wearing beggar tells his story.

A village where the royal family lived in peace.

However, a group of people suddenly appeared and attacked the village, killing people and raping women while laughing and taking over the village.

Even if you run away in the middle of the night and ask for help, it's no use, and you end up hanging at the government office and getting beaten up badly-

"Wait a minute, are you saying that the government beat that face to a pulp?"

"That little rat who doesn't even pay taxes was bothering me, sob."

However, such small villages do not pay taxes.

It's because they usually hide in dark places, and even if they get caught and tell you to come out, they just say, "Cut open our stomachs, we have nothing," and that's it.

Because they don't actually have anything, there's no point in messing with them, so they call them rats and don't even treat them like people.

So, although the beating was severe, the official must have had something to say.

When I told them not to bother me because they wanted to live among themselves, they said that when something happened, they would come looking for the king.

The beggar burst into tears, as if overcome with sorrow, and it was difficult to tell whether he was speaking or sobbing.

However, I think I know without hearing any more.

Qing's eyes become fierce.

"Is Wanggachon the village on the northern ridge?"

Jeomsoi answers on behalf of the sobbing beggar.

"Miss, that's probably Danga Village. Wangga Village was a remote village half a day south of here, at the foot of a mountain."

His eyebrows twitched.

So it's a different village?

Are you saying there are other guys who come in and kill people right away?

"That lady, I've heard it's a huge sect called Gangpaecheon. If you get involved, you'll be in big trouble."

"Please, kekekeke, help me, please……."

He looks back at Tian Yuxue.

"Kang Pae-cheon? Hmm. The Ten Great Sects? Is that right?"

"Let's call it something like that. What? The Ten Great Natures of the Apostles. Even the Sapa guys made it so they could count the ten, but it's not something to be taken lightly. Sigh. They won't listen if you tell them to stop anyway, right?"

"Well, if you're serious."

At that, Tian Yuxue sighed deeply.

"Think carefully. This was a different matter from simply dealing with the local demons. You can't afford to leave any regrets. For your own sake, too."

The story of the monk made my heart flutter.

Chen Changming grabs Qing's sleeve.

When Qing looked down, he turned his head.

To Chen Changming, the members of the Shinnyeomun family were much more precious than that mere apostle or whatever.

But does that mean we should ignore such human beings?

Would Master want that?

Qing strokes Chen Changming's head.

"It's okay. How would they know who we are? Um, was Yeonyong okay?"

Yeonyong was the pseudonym of Murong Zhuxi.

The eldest daughter, Eonyeonyeong, the second son, Eonyeoni, and the second daughter, Eonyeonyong.

If you pronounce it simply, it's "Eonyeo-nyeong, Eonyeo-nyong."

Of course, except for Unyeonyeong, it's different from the actual historical facts as it's Qing's creation.

However, using a pseudonym was not actually that easy.

In fact, the biggest reason for being caught using a fake name was because people don't understand when I call them.

When you use someone else's name, it feels like you're calling them by their name, so you can't understand it as easily as when you call them by your own name.

"Hey girl?"

"Oh. Yes. It's me, it's me. I, I want to go with you, sister."

When Unaram called, it was a song that gave me goosebumps a hundred times over and was unbearable.

But Changming'er sings it often, and Murong Ju-hee's singing was somewhat tolerable.

Why?

Hmm? If Changming'er calls, it's okay?

Qing thought about it for a moment and said, "Yes."

It seems like there's not much resistance to hearing it from a kid.

The rag-faced beggar looks up at the group with a dumbfounded expression.

"Are you saying you will help me……?"

"Don't expect anything in particular. If you get entangled in something, you'll get in trouble, so don't open your mouth. You know what I mean, right?"

"Even if it's the name of your benefactor-"

"Didn't you hear what I just said? I told you not to get involved, and you already asked my name and sat down. Just get moving. People can get really puffed up like hotteok. Hmm, I want some hotteok. Is there a hotteok place around here?"

----

There was no hotteok shop.

So, justified anger covers Kangpaecheon!

The enemy of hotteok! I'll kill you all!

"Those guys wouldn't have annihilated a village for nothing. Their goal was probably the village itself, not information. They plan to use it as a base for a long time."

After climbing the mountain, they must have realized that this exploration would not be over in a day or two.

In this situation, coincidentally, there was a village located right at the foot of the eastern mountain of Mount Lao.

There was a shabby house inhabited by people in a prime location that's easily accessible from any mountain range in Mount Lao. How great would it be to use it as a base?

"Hmm. They're really killers."

"This was why we must get rid of treasure. When someone who was not human becomes greedy, this was the kind of wickedness they exhibit."

The more you know about the world of Sapa, the more surprising it becomes.

Are they human babies?

"And if they need a stronghold, it must mean they're quite numerous. If there were only a few, why bother? A gang like Gangpaecheon wouldn't want to build a reputation for destroying villages, so they'd probably just occupy the best house and rule."

"Hmm."

"But it's morning now, so most of them have probably crawled back into the mountains. The ones left are either worthless rascals, or the heaviest of the bunch, too lazy to do the dirty work."

Chen Changming and Murong Zhu Xi's gaze naturally turned to Qing's lower body.

Qing's gaze naturally turned to Murong Zhuxi's wide pelvis.

"What? Why? Are you looking at me? Well, let's say Miss Murong was like that. Why are you looking at me, Jang Myeong? If you're going by the prominent curve, shouldn't you be looking at Miss Murong here? It's stretching out from the waist like this?"

Qing pushes his hands horizontally left and right.

At that, Murong Juhee blushes.

"It's, it's not that bad."

"Huh. My sister has a bigger butt."

Chen Changming speaks with a proud tone.

Of course he's tall, so he's taller.

To begin with, Miss Mo-yong was only about as tall as my shoulders, so it would be weird if her butt was bigger.

When saying that someone has a big butt, he insisted that rather than the absolute mass, one should consider the proportion of the buttocks in the body, and the shape of the curve, whether it's a crescent moon or a sagging moon, and that one should strictly distinguish between the size of the buttocks and whether they are pretty just because they are big.

Tian Yuxue adds his opinion to it.

"What's the big deal about the butt? Seriously. Huh? Seriously. Are you kidding me even this far?"

"Hey, if you're too tense, things won't work out, so I'll lighten the mood for a moment."

Anyway, Qing was impressed.

Doesn't the fact that the village was raided bring out a whole series of things that have been discovered?

Honestly, I don't get the impression that the teacher was particularly smart in his words and actions. As expected, being a lecturer, or a professor, isn't something just anyone can do.

"So, are you saying that there are only small fry, or there was a strong one among the small fry? One of the two?"

"Since the Sapa guys are so good at playing, they can't stand to see their subordinates playing, so even if there's a strong guy, there's probably only one."

"Well, then I'll make a little noise at the main gate. Jang Myeong and Lady Mo Yong can use that gap to climb over the wall, and Master, you can do whatever you want. And don't leave any trouble behind."

The look in Qing's eyes as he speaks was bleak.

Don't leave any regrets behind,

It means let's kill them all.

At that, Tian Yuxue sighed deeply.

"Ha. I don't know if this was the right thing to do. My master was gone, and I don't know what to say to the ancestors."

It was a lament that the new Divine Thief were meant to steal lives rather than wealth.
