\chapter{A sad legend, what kind of legend was it? (4)}

Regardless, the dual-wielding swordsman snorts and gently draws his sword.

Ssrurung, the sharp blade makes a refreshing sound as it draws a large circle.

Oh, doesn't that draw the sword so nicely?

Qing was a little impressed by the sight.

"Seoho's horny dog ​​can't get rid of his bad habits and is trying to seduce women here too."

"What the hell? You horny little shit? How dare you, you think I'm-"

Pounce gets angry and shouts, but his words are cut off mid-sentence.

"Who are you? You horny little shit who only trusts in your father's back. You think your good father can protect you even in the land of the dead?"

At that, Pounce hesitates and his momentum was severely reduced.

But the mouth was less bent.

"Do you dare to insult the Iron Blood Gate?"

"A dog only barks in its own territory. If it ventures outside, it'll only get eaten. Why, you want to try with a knife?"

Pounce rolls his eyes.

Strong and weak are the characteristics of Sapha and Qing.

The twin swordsman was so strong that he hesitates.

There are already several famous madu in the city.

But you don't care even after hearing the name of the Iron Blood Clan?

Then, wouldn't it at least have a higher level of support than the Iron Blood Gate?

"Tch, this was ruining the mood. Let's go. Tch, this was going to be unlucky."

Pounce spits and turns away, pretending to be offended.

They said it was Chiljeol, but the large family of six siblings had all rushed out and left, leaving only the twin swordsman alone in the place with a look of disappointment on everyone's face.

"Oh, was that the famous Madou just now?"

"Not to the point of being a madman. He's just a half-assed bastard who lures women with his good family background and attractive looks, then teases them to his heart's content before dumping them when he gets tired of them. Well, those women who know everything and still fall for him, thinking he'll be different, are also a problem."

A handsome man from a good family seduces a woman, and in the expression of his hometown, he was called a "meokbae."

"It was a bit ambiguous. Um, thank you for helping me."

"No. I came here because I heard a familiar name, and some rascal was talking nonsense. You said your name was Unyeonyeong?"

"Yes. But?"

"Hmm. I guess they were namesakes. Then."

His eyes sparkled with laughter.

Come on, this was the guy who knows Unyeonyeong, right?

Are you a member of the Blood Cult?

But for something like that, the text was blue. Why was it a good thing? Isn't it even tall?

It was very suspicious and doubtful.

He looked the man up and down.

Oh, my.

Twin swords. Small stature even with a shield.

A flat and firm chest.

However, the size of the pelvis was enormous.

Looking at the magnificent scale that almost rivals my shoulders, one person suddenly comes to mind.

Meanwhile, the twin swordsman nods and turns around.

Qing then grabbed the unmanned vehicle in a hurry.

"Excuse me. Since it was fate that you helped me here, could I buy you a cup of tea?"

"Yes? No, I didn't do it expecting anything in return, so don't take it to heart."

"Hey, don't be like that. If not tea, then alcohol? How about a glass of jjimuknoju with fish cake soup? Or, how about a glass of jjimuknoju with fish cake soup?"

He sees the fish cake bowls piled high in the street stall behind the unmanned building.

"……It's still sunny, so you're drinking alcohol?"

"Then I guess we can drink until the sun sets? Okay, don't do that. I'm just grateful."

"I'm sorry, but I don't feel like it."

"Oh, are you going to keep pulling it out like this?"

Muin tilts his head, thinking that he has heard that line somewhere before, but was startled by a voice that suddenly clings to him and whispers in his ear.

-Miss Murong? Is that Miss Murong?

"Who was that…?"

"Okay, okay. Let's go. Alcohol? Tea? Snacks? I'm hosting a benefactor today, so let's enjoy it without limits. Okay, okay."

The unmanned person then links arms with him and, unable to shake him off, drags him away.

The onlookers also just made strange expressions, as if they were seeing it twice.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As soon as he entered the inner room of the tea house and the unmanned person took off his hat, the beauty of Geomhwa was revealed.

"Oh my goodness, we all meet in a place like this. How have you been?"

But Mo Yong-ju-hee uses all her brain power to ask, "Who was this person who pretends to be friendly?"

And the identity of the boy who was standing right next to her and glaring at her like a poisonous snake was also completely unknown.

However, the social skills honed at the Yongbong branch do not go anywhere.

"Uh, um, Miss Yoo? Am I right? Oh, am I not? Uh, if not, I'm sorry."

It was a roundabout way of saying that you don't know the name.

If he knew the name in the first place, even Murong Juhee would have recognized it as soon as she saw it.

So, I wonder if there aren't a few women from small and medium-sized businesses who haven't met each other.

And wouldn't the women of the small and medium-sized sects have always been anxious to look good to the hostesses of the Phoenix Society?

So it's not exactly strange that I'm so happy, but-

"What, you already forgot? It's me, Ximen Qing."

"yes?"

"Oh, I'm in disguise. How was it? Looks perfect, right? You wouldn't recognize me, would you? No, I already didn't recognize you."

"Huh? Now that I think about it, but, Miss Ximen, this was it."

Mo Yong-ju-hee raises the back of her hand in front of her chest and makes a motion as if she was scanning something.

"Ah. This was also a disguise. Now, look."

Qing opens my front pocket and reveals a tightly wrapped bandage.

Chen Changming pokes Qing's side.

"who?"

"This was Chen Changming, the youngest of the Shinnyeomun clans. Changming, greet me. The Sword Flower of the Five Flowers of the Martial Arts, Lady Murong Ju-hee. My friend."

"friend?"

The venom drains from Chen Changming's face.

"Hello. This was Chen Changming. I am indebted to your private tutor."

At that, Mo Yong-ju-hee blinked her eyes.

"Miss Ximen? Are you the lady?"

"Take that off, sir. What was it, young lady?"

Then, Murong Juhee's face brightens.

The flowers that were pale and withered suddenly bloom, and their beauty rises to the point where it feels like the room was brightened.

Chen Changming's eyes become sharp again.

Regardless, he moved his hips across the table, sat next to Qing, and leaned against her, placing his arm between them.

"Hehe. Ugh. How have you been?"

"I've been doing well. How's Miss Murong? Are you feeling better? Are you sleeping well?"

"Thanks. I'm better now. No, um, uh, but I'm still not sleeping deeply, uh, if it's okay with you, Miss Ximen, uh. Tonight, uh…"

Chen Changming's eyes become sharper.

But Qing isn't really interested.

"I'm glad to hear you're feeling much better. But what's going on here? Did Lady Murong come here to find the Absorbing Magician?"

At that, Mo Yong-ju's eyes widened.

Of course, Chen Changming's eyes remain sharp.

"Are you talking about the magic of absorption? The magic of killing? Why that vicious magic…?"

"Huh. Didn't you know that?

"I just came out to get some fresh air. Somewhere I don't know anyone, that's it! Well, sometimes I just want to be alone. I'm fine, but I'm just feeling a little… so we're close…"

"It's okay. Everything was okay."

Qing gently stroked Murong Zhuxi's back with a pitiful heart.

However, when I heard the surprised sound of "Haauk," I thought, "Oh, this isn't it."

However, when Murong Juhee, who had been leaning forward awkwardly, hung on with even more weight, he suddenly reached out and seemed surprised.

"Hmm. You wanted to be alone, so I guess I should've pretended not to know."

"No! If it's you, Miss Ximen, I really wanted to see you. It's so reassuring to have you by my side. I like it…"

Mo Yong-ju's expression was bright.

In fact, the previous Murong Zhuxi was always sick.

You might wonder if having a little heart was something that seriously hurts, but it was a truly hopeless wound to me, so it always hurt.

So, I use a sharp blade and stab it.

Those bitches with breasts, they think it's okay to take some abuse from me.

But after you've been really hurt, and someone's been there to hold you while you're being stabbed by those thorns.

Murong Zhuxi also had a great realization.

Everyone has a point of pain and wounds, and that pain, whether big or small, was extremely painful for them.

I feel so ashamed of myself for being so cruel to others, demanding that they know I was in more pain, but on the other hand, I also want to be someone who can be a comfort to others.

So that's what I did.

Strangely enough, after doing that, people started to flock around me.

When I'm around people like that, my pain subsides and a smile naturally appears.

But still, sometimes it hurts.

I felt so angry that I thought, "Someone should understand my pain," and so I went out to get some fresh air by myself.

"lol……."

Haven't you met someone who understands your pain?

It's Mo Yong-ju-hee gently rubbing her cheek against his forearm.

And yet, it seems like he's checking the mood to see if it's okay or not.

There was a hint of worry on Qing's face.

Is this okay?

The way you speak was like that too.

As if the person had become a child, well, isn't it still very painful?

However, what Qing did not know was that Murong Zhuxi's reputation had completely changed and was rising vertically, rising in real time.

Suddenly, he became more mature, his face became gentle and dignified, and he became more mature.

She's short, but she turned out to be a pretty girl.

But even older sisters have people they want to show off to.

But Qing doesn't know the circumstances.

There's no way Murong Juhee would be ashamed to say that she became that adult herself.

"Jangmyeong, why are you here again? Don't rub it, the scar will fall off."

"joy."

A situation where small things on the left and right are rubbing your cheeks.

Well, they both have the right to be spoiled.

Qing asked, shrugging it off as if it were nothing.

"By the way, do you know Unyeonyeong?"

"Well, you're a traitor, a spy of the Blood Cult."

And before the betrayal, he was a patrolman of the Wulin Alliance and a member of the Jinju Eon family.

So, if the 10th generation of the Gupaebang was the latter, it's impossible not to know.

"oh."

It was only then that Qing realized the huge blind spot in Unyeonyeong's impersonation.

It's nice to turn a blind eye, but I never thought about being more popular with the political people.

Hmm. I guess I'll have to be more self-restrained from now on.

You should only impersonate someone when absolutely necessary.

"But, I think you said it was a magic absorption technique……"

"Ah. They say there's a hidden treasure in Mount Lao. And they say the treasure was a magic absorber?"

"Ah. The city seems to be full of martial artists. Shouldn't we report this to Maeng immediately?"

"It's too late. If we tell them now, it'll take at least two months for the Wulin Alliance's investigation team to arrive. In two months, they'll have dug up every tree in Mount Lao."

"So, was the reason you're here, Lady Ximen, to find that magician?"

"I wanted to find it and get rid of it. If possible, do it secretly. That's why I disguised myself like this."

At that, Mo Yong-ju's expression becomes determined.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As I returned to the guest house and lay down in the room, around dinner time, Tian Yuxue suddenly opened the door and barged in.

"Oh my, it's okay, it's okay."

"Oh, Master. You're here?"

When Qing suddenly got up, the two people who had been clinging to him in the cold rolled over on the bed.

Because Qing's abs, which are as strong as iron for a thousand years, have the strength to throw away two kids who are lying down.

"Hmm? What was it? That girl?"

"This was Lady Murong Zhuxi of the Murong family. She said she wanted to help find and eliminate the Absorbing Demon. Ah, Lady Murong. This was my second master. Uh…"

"You can call me Master Tian."

After exchanging a brief greeting, Tian Yuxue unfolds the map.

"This was Kyoho Peak, the highest peak. Usually, when people refer to a stele, they're referring to the highest peak, so it's a strong candidate. Even if it's not, the surrounding scenery will be beautiful."

Then put your hand down.

"They say there's a strangely shaped, square rock formation here called a natural rain. It's so obvious, I doubt it's here. If it was in such an obvious place, then maybe the magic would have vanished long ago."

Once again, Tian Yuxue was snapping his fingers.

"They say there's a big cave here, here, here, so let's stop by on the way to Kyoho."

With a map, a pretty plausible plan can be created.

If you have a map like this, you should have gotten it a long time ago.

But where did you get this map?

Then suddenly, Qing discovers a red seal stamped on the corner of the map.

The conductor.

Hmm. You came back after clearing out the Dojihwisa Gunmaek.

For reference, a commander was the commander of a province who commands approximately 60,000 to 80,000 soldiers.

Qing quietly folds the end of the map so that the seal was not visible.
