\chapter{A sad legend, what kind of legend was it? (5)}

I thought Tian Yuxue didn't say anything.

While Qing was going to the side room, why did you come to the side room first?

Were you in that hurry?

That's not the point.

What's important now is-

"How's the side room? Is it clean?"

"I don't know. The side room in the commander's quarters over there was really shiny."

"Oh. Where was that? Can you come back right away?"

Since the internal state of the side that has not yet been entered cannot be known, it can be said to be a superposition of the quantum states of clean and dirty.

Until Qing opened the door and began to observe.

However, since there was no toilet association in Zhongyuan, the conditions are generally quite dire.

"Enough with the rumors. Why did you bring that kid? He was in the Blood Cult's basement back then, right? Well, that aside, if you're going to ask dogs and cows to go with you, you should've gathered everyone you know and formed an army when you visited the Wulin Alliance."

"Back then, I didn't know the rumor would spread so far. If I had known, I would have come with the Wulin Alliance combat unit and looked into it."

"Yeah. But still."

"Hehe, with all the bad guys in the city, how could they leave a weak, fragile girl like me alone? I know from experience that if you're a beauty as beautiful as the Five Flowers of the Martial Arts, there will be guys who will rush in and eat you, even if it means dying."

"Hey, what's a girl eating? Why don't you speak more politely? Wait, wait, have you ever experienced something like that? Are you saying you've ever had a bastard like that? What kind of a bastard would do that?"

He told me to speak nicely, and then that idiot popped out.

For reference, Yuksi was a punishment in which the grave was dug up and the head of the corpse was beheaded.

You might say that there's no point in dying again when someone was already dead, but if you're going to be punished by the Sixth Sense, then you've already destroyed the entire clan.

So, it includes the meaning that the surname should be completely wiped out.

"Hey, am I the kind of person who deserves to get hurt? Anyway, it's obviously dangerous, so I can't just pretend not to know."

"Tsk tsk, anyway, with such a soft heart and such a backslider attitude, how can you possibly navigate this harsh world?"

When the disciple (Cheonsalseong, the pleasure killer) who was soft-hearted and withdrawn smiled apologetically, Tian Yuxue had nothing more to say.

"Even a single piece of paper was better than nothing, so wouldn't it be better if we did it together? If we team up with Changming, we could probably do the job."

Even though Qing said it with her own mouth, she was still laughing.

"Isn't it? Even if two people who are only first-class and barely peak together combine their strengths, it's only first-class and peak, so expecting them to be at the peak level was a bit much."

For reference, one serving of Qing was super-large.

Even Lady Murong would do half the work, so Changming'er must be relieved.

But if you put the two together, it's half and half, um, if it's first-class, maybe three or four pennies? Two pennies? Wouldn't that be enough power?

Anyway, the side was terrible.

Well, it's because time was the time zone.

Because of the nature of the inn, since they have rooms on the upper floors, they are a paradise for people to drink freely, so after dinner time passes, um.

Wasn't it true that one of the long-standing customs, traditions, national characteristics, and behavior patterns of the Chinese people was to relieve oneself on the street?

I feel like I understand why that's.

They say people's hearts are deceitful.

Mo Yong-ju-hee smiled bitterly.

I felt so relieved when I saw the blue.

Rather, I feel more at ease than when I am alone in my room at home.

It felt like the thorn that had always been stuck deep inside me and made me feel sick, the deep wound that I had never told anyone about, was healing.

So I couldn't be happier about being allowed to stay with you.

"Excuse me, Miss Ximen?"

"Huh? Why?"

"Ugh, you know. Ugh."

"What was it? I have to tell you."

"That, that. So……."

Mo Yong-ju's voice creeps in.

Then, with a face flushed red, Mo Yong-ju-hee lowered her head and said, "No, no."

Now that she has no reason to go out, she has taken off her disguise and was now the Ximen Qing that Murong Juhee knew. Now that she has seen Qing, she cannot bear to think of anything else.

The voice that keeps ringing so clearly, the sweet voice that was gently wrapping around my ears, well, it's a little prickly, prickly.

The cold, snake-like touch of that moment, the blazing fire that pierced every bone, muscle, and nerve of my body like a lightning strike. As those claws tightened, as if biting—

"Miss Murong?"

"Ugh, that. No, no."

When we broke up, I decided to be honest and confess and ask for favors, but how could I actually bring this up in front of him?

Murong Zhuxi was red-faced and doesn't know what to do.

Qing looked at the sight and suddenly…

And inside the Qing dantian.

A tiny blue dragon wrapped only in thick rope and shining cotton, Hwanhee Jinki constantly swings his long, plump arms and legs.

There, a small, blue-haired demon wearing a black robe with a sinister eye pattern was crouching with his head held in his hands, being beaten.

With large teardrops hanging from the corners of his eyes, he muttered, "Heuk, Heuk."

The Heavenly Demon True Qi was laughing… … .

Hwanhee Jinki has nothing to do these days.

Before, when I was accompanied by a compatriot, a big-hearted, strong woman with the same spirit of joy, I really enjoyed the work.

But no matter how much I try to incite the little one next to me by turning his killing intent into a lustful desire, he was blocked by a firm defense that says, "Baby, baby, you have to protect me," and I cannot be guided.

So, if you pile up a grudge that has no place to be resolved, it will only become poison.

So, Hwanhee Jinki has nothing to do and no motivation, so he just sits there and lazes around.

Hehe, that annoying laugh.

Why can't that rotten, moldy, foul aura stay still? Will it go away if I hit it?

From then on, Hwanhee Jinki continued to play and pass the time.

Then, the entrance to the dantian suddenly opens and the true energy that had stopped by the upper dantian rushes in.

I wonder what he's so busy with. He puts his hands on his knees and catches his breath for a moment, then kicks open the exit door and runs out again.

A man wearing a Shaolin robe draped over only one shoulder leads the way.

After that, the Bannya Jingi, who was clearly tired, rode in a palanquin wearing all kinds of jewels in the Indian style.

Hwanhee Jinki suddenly feels something strange.

Why was he panting while riding in a palanquin?

As the work of the Hwanhee Jinki disappeared, the Jinki of the Buddha and Taoism changed their strategies again.

If you can't stop the killing, it's better to kill the wicked and let them die.

So, while the Taoist energies were protecting the spirit, the two Buddhist energies were actually encouraging the will to kill, saying, "If I don't go to hell, who will?"

Suddenly, Hwanhee Jinki tilted his head again.

But which Jin-gi proposed this strategy?

That was when.

Hwanhee Jinki's ears perked up. His nose sniffed.

This feeling! The sound of obscenity! The smell of obscenity!

I have something to do!

Originally, true energy was meant to flow without stopping.

In other words, they are extreme workaholics.

This was actually the reason why other true qi beat up Heavenly Demon True Qi.

It doesn't flow, it's stuck to the dantian, and it blooms like mold, so to the true spirits, why on earth does it not move and just take up space?

Hwanhee Jinki leaves behind the Pacheon Magic that was being defeated and hurriedly runs out of the Danjeon.

The only remaining demon left behind is, ugh, ugh.

And the Wolnyeojinki, who always watches, stares blankly at the sight.

Murong Zhuxi was red-faced and doesn't know what to do.

As Qing looked at the sight, her eyes suddenly widened and she looked strange.

"Miss Murong? Do you want to come here and see?"

"Yes? Yes, yes."

"Answer only once."

"yes yes!"

"Oh, why aren't you listening?"

At that, Murong Juhee swallowed her saliva.

Then he slowly moved towards Qing and tried to sit next to him.

"Eek."

Suddenly, I felt a strong force pulling me forward, and then a firm, soft feeling, different from the bed, was placed under my buttocks.

Murong Zhuxi was embraced in Qing's arms.

Murong Zhuxi felt a great sense of comfort.

But that was only for a moment.

The hissing, snake-like whisper that burrows into my ear makes me harden like a stone.

"Miss Murong? What were you trying to say? If you keep saying that, I'll be curious. If I'm curious, how can I sleep? Miss Murong, you've had a hard time sleeping, too. I wish I could do the same."

"No, no. That's not it-"

"Ssup. Answer only once. Why don't you understand? Not twice, not three times, just once. Do you understand?"

"yes."

Gulp. Mo Yong-ju-hee swallowed.

Then he opens his mouth and adds:

"yes."

"This. Do you think you're doing this on purpose? Are you not going to listen? Why did you become a bad child? Bad children deserve to be punished."

Something cold seeps under his jacket.

A hand gently stroking the stomach.

Then, the thumb rubs about half an inch upwards and wipes it off, and then the cool palm follows and runs up the stomach.

That hand slowly rises once, once again.

Mo Yong-ju-hee's jaw was choked.

Finally, he reached the pubic bone and his thumb gently rubbed the hard bone above it.

Hib.

Mo Yong-ju-hee bursts into hiccups.

A soft laugh echoes in my ear.

"Make a sound like a trampled frog. Then which way should I go? Right? Left?"

Right, left, in time with the whisper, the thumb sweeps around once to the right and once to the left.

"Uh, as Miss Ximen wishes-"

"Oh, I can't. You have to be clear. Do you like the right or the left? Tell me."

"Well, then, hib, ugh……"

That was when.

A hand that slips away mysteriously.

Mo Yong-ju's expression becomes pitiful.

"Miss Ximen? Hi. Why, why…?"

"I think Changming was coming. Young Lady Mo-yong, you should wash first. I like to stay warm. If I go in first, this angle was basic."

He gathers all the courage he has to have to have courage.

"If we wash together, together-"

"No. You answered twice on purpose earlier, didn't you? A naughty child has to wash by himself."

After saying that, Qing lightly pushes Murong Zhuxi away.

And then he lies down on the bed with a large spoon.

Mo Yong-ju-hee fidgets and looks around, not knowing what to do.

Qing bursts out in a lighthearted laugh.

"Hey, just kidding. Just kidding. What's Miss Murong like in the first place? The bathhouse here was so small that it's hard to even get in alone. But if I go in first, the time and moon won't come out, so Miss Murong should wash first. Anyway, if we go up to the mountains tomorrow, who knows when we'll be able to get some hot water and bathe."

It's a cheerful and cheerful atmosphere as usual.

However, his eyes are unusually clear.

It was so clear that I wondered if it was originally that clear.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Wake up early in the morning and take a look at Murong Zhuxi's disguise.

"This, this."

Mo Yong-ju-hee's voice trembles faintly as she looks at the meaning of the Divine Thief Vision.

"What kind of monster was this? What kind of divine creature was this in the world…!"

Then, he takes it with care as if he was handling the most precious thing in the world, and caresses it very carefully as if it were his lover's heart, wondering if it will burst if he pushes it or if it will pierce if he pokes it.

Chen Changming, who was looking at the scene with a pout, asks Tian Yuxue.

"Why am I the only one dressed as a man?"

"Huh. This. Have you ever heard of the term 'original version'? If that child disguises herself as a man, anyone would immediately think she's a woman disguised as a man. That's what makes her suspicious. In that case, it's worse than not disguising at all."

She said she was too pretty to cross-dress.

The tendons on Chen Changming's forehead crackled.

Qing hugs Chen Changming in her arms.

The size of the JinChangming has to be just right.

If you drag it into your arms, it's the perfect height to put up a useless, warm lump of flesh.

"It's heavy. Put it away."

"I carry it around with me all the time. Can our handsome Changming'er be patient with me?"

His tendons flared up.

"I can become prettier if I go to the peak."

"Even Lady Murong hasn't completely transformed yet. And Changming'er was a first-class reviewer, and Lady Murong was a peak reviewer. Who would do it first?"

"I hate you. It's too much."

"Huh. If you only cared about looks, Changming would have abandoned you the first time we met. Come on, let's get ready."

So, I finished my disguise in the morning.

The herbalist's attire has been lowered from perfect herbalist to less perfect herbalist due to changes in the search policy for Mount Lao.

So I bought used clothes and washed them well, so they were dirty but clean and didn't smell.

Pack your clothes.

Take good care of your new suitcase.

I put all the rice balls I'll have for breakfast and lunch in it, put on my uniform, and leave the room.

Now that we have a map, we plan to climb up the northeastern ridge of Mount Lao and climb up to the nearby peak, Cheonwonbong, to take a look.

So, this was the start of the treasure hunt.