\chapter{A sad legend, what kind of legend was it? (7)}

A rag was still a rag, no matter how much you wash it.

But it doesn't smell.

The newly woven dorongi are less dead and more durable.

But it doesn't smell.

Yeah, the day before yesterday wasn't that great…

With a net and a stick, a perfect mountaineer was born.

People are sad beasts who judge others by their clothes, not their content.

Disguising a knife as a stick was so easy that even a child can do it.

First, find a long, straight piece of wood that can accommodate the blade. If you don't have one, you can chop it down.

Two. Lightly wrap the wire around the base and then insert it straight.

3. Just cover the handle with a dirty cloth or something and you've got a perfect stick!

If you prepare the ingredients, even a seven-year-old child can make it.

Oh my goodness. There are two worthless people in this group who can't do this.

Qing climbs the hill while lost in thought.

Halfway up the hill, a wide, flat plain appears, and a fortress village with a wall made of buildings appears.

A location where it's obscured by a hill when viewed from below, and by a dense forest behind when viewed from above.

It was truly a hidden village.

Qing approaches the entrance with a calm demeanor.

The river basin was the 19th highest in the Gangpaecheon River system.

A more familiar term for the people of Zhongyuan would be the nineteenth disciple of the Yi family.

There was a reason why he was called Lee Gye-wi instead of Lee Dae-jae.

It was because when you reach the age of 10, you have to be different from others.

Of course. I don't know how much of a difference it makes from others when you call an elder "Cheon Seung-in," a first-generation disciple "Ilgye-wi," a second-generation disciple "Iggye-wi," and a third-generation disciple "Hey, you little brat over there."

Anyway, the riverside man on the other side saw a man dressed in a straw hat at the bottom of the hill.

There's a tall, sturdy thing coming up there, using it as a cane. Is that a cane or a weapon?

It's confusing whether it's unmanned or not.

The riverside guard cautiously calls out to the man who was lying down on the ground.

"Sign language, brother."

There was a big difference when you call him Lee Dae-wi instead of Lee Dae-jae.

If you divide ranks by a certain number of ranks, you end up creating a superior-subordinate relationship that's even more cruel than the distribution relationship tied to the death penalty.

Brother Su-hwa was in 17th place.

It's only a two-step difference, but in the hierarchy, the lower-ranking ones tend to care more.

I dare not touch the senior warrior.

I can't even scream loudly.

You have to wake them up by whispering little by little.

"Sign language, brother."

"Huh? Huh? What was it?"

"Someone was coming."

"What was it? Who was coming?"

"I don't know."

"Don't you know? Moolah? This kid's going to get away with it. If you don't know, was your life in the underworld over? If you don't know, was that all? You punk, if you don't know, you should find out. If you don't know, should I find out and tell you? You're a punk who'll eat up organizational life."

It's a sound that destroys common sense.

If the subordinate doesn't know, isn't it natural for the superior to find out and inform them?

That was why they are respected by being called seniors, seniors, and superiors.

Just being born first or being initiated first was not a reason to be respected.

But originally, Sapa was someone who pioneered a different path that others did not take.

That's why the apostles.

Those who walk a different path!

"I will look into it."

"You little shit, you dare wake up your brother from his deep sleep? You fucking punk, why don't you come down here and get on top of me?"

It's clear who's the more clueless one among the guards who spot the guy and the suspicious person and report it to their superiors.

And the set was bullshit.

Surprisingly, there was only one person between the seventeenth and nineteenth positions in the hierarchy.

And a gathering refers to the act of calling together a large number of people.

If you were to call out the 18th rank in the hierarchy, it would be clearer to call it a call rather than a set.

For that reason, the riverbed was swollen.

But the facial muscles trained through long-term training do not show any signs of fatigue.

The river captain puts his head into the eye hole in the wall to find out the identity of the person who caused the disturbance.

A suspicious person who comes leisurely as if he has come to drink something.

But as we get closer, the suspicion disappears.

I wonder if it's really necessary to wear a hat overturned, a bag hung on the back, and a cane that's so thick and sturdy.

He's just a common hunter.

"Brother. I think you're a mountaineer."

"What? Same? Are you supposed to report vaguely?"

"I am a mountaineer."

"Is he from this village? Take care of it yourself. No. If he's a mountaineer, just catch him."

"yep."

The riverbed heads back towards the eye socket.

And the leisurely pace of the hunter was mind-blowing.

Thump, thump. I walk, peering at the grass on the side of the road, and then a butterfly catches my eye, and I take another step, another step, and—oh, thump!

The riverbank cannot stand it any longer and jumps down.

He quickly approaches with a sharp and sharp sword and aims it.

"Who are you?"

The hunter falls to his knees.

Kneeling and begging was the most popular means by which the common people protect themselves from the sword.

"Oh my, Nari. What's wrong?"

"Hmm? You were a woman? Anyway, who are you, and why are you here?"

"The girl said hello and was just going home."

The riverbank smiles at him.

"This was really suspicious. Show me your face."

The hat of the dorongi that climbs up to him.

A woman with a crooked nose and a worn-out appearance.

Still, a beauty that cannot be hidden sweeps over you.

A veritable storm of beauty.

The riverbank was gripped by the illusion of facing the strong wind head-on.

"Ahem, this was still suspicious. Are you hiding something dangerous?"

"Dangerous stuff, that kind of thing—"

"Okay, I need you to take off all your clothes and kneel down quietly so I can search you."

Searching women's bodies was a hobby of Sapa.

The woman protests to him.

"How can you ask me to take off my clothes in broad daylight, Nari, please?"

"Oh, does this old man have to take it off himself?"

"Then, if I just take off my clothes, you can let me go-"

"No. Isn't there a hole for hiding things? I should search mine too."

"Nari, please-"

"Why was it so hard to take off your clothes? Then I guess I, the old man, will have to help you."

The riverbed stretches out its hand, snorting with breath.

The woman also snorted and stretched out her hand.

Surprisingly, the woman's hand, which had been extended later, touched Hacheondae first.

This was the principle of latecomer.

The hand that stretches out vertically with the index and middle fingers touches the nape of Hacheondae's neck.

Fingers are inserted one joint at a time between the collarbone and about an inch above it.

"100 million."

It was a riverbed with two holes in the prayer room.

The air passes straight through the cavity close to the lungs, without passing through the nasal cavity and pharynx, and was surprisingly refreshing, opening up the airway.

"……!?"

However, the moment the air stops flowing through the throat, a person cannot make a sound.

If there was one hole, it will make a half-leaking sound, let alone two.

"I was worried that they might be normal, but they are, as expected, Sapa bastards."

The woman's hand turns horizontally.

The flustered Ha Cheon-dae was about to grab my neck, but this time a flesh-colored pillar suddenly approached me and slammed into me.

A terrible, excruciating pain that seemed to pierce both eyes.

At the same time, the world was plunged into a pitch-black darkness, like a room with a candle turned off.

"……!!!"

The riverbank catches my eye.

The warm liquid flowing down the cheek has a thick viscosity, unlike tears.

In front of him, the woman spreads her arms out with her palms outstretched.

And clap your hands!

However, this was not the sound made by hitting palms together.

It was the sound of a strong slap to the left and right as the head of the riverbed was hit by the wind.

The palm presses down on the earlobe, and the compressed air enters the ear canal, popping the eardrum!

My throat was clear! My eyes are clear! My ears are clear!

A colorful wind blows fiercely from the prayer hole.

If it had reached the vocal cords where it was supposed to go, it would have erupted into a truly desperate scream.

The invisible and inaudible riverbed sheds tears of blood and lets out a silent scream, when suddenly I feel a hand grabbing my forearm above my elbow.

And then, ah, ah.

The colorful air leaks out again.

Woman, Qing has a subtle expression.

Hmm. I'm really discouraged because I can't hear the screams.

Why, when you watch actors copulating on screen in your homeland, isn't it just not fun if you turn off the sound?

Still, it's quite visually rich.

An unknown Sapa warrior, all he knew was that he was a nympho skilled at flirting with women. The bones below the Sapa warrior's shoulder were crushed, and his arm was limp.

Wouldn't you be rolling on the floor, not knowing what to do, with blood flowing from your eyes and ears?

Hmm. It's a bit disappointing.

Qing kicks the ground a few more times with his toes, completing the Chilgongbunhyeol.

For reference, the term "chilgongbunhyeol" means bleeding from seven orifices: two eye holes, two nostrils, two ear holes, and one throat.

Qing grabs the bastard by the collar and approaches Dan-ga-chon.

Because he was bald, he had no choice but to grab him by the collar.

I understand why he's bald, seeing as he told me to take it off earlier.

The Sapa warriors are fighting to start a fight, but after becoming blind, deaf, mute, and paralyzed, all they can do was kick their legs.

The Qing dragged itself to the front gate of the fortress village.

Why was it so quiet?

Haven't you seen what happened to your family?

Don't you think it's strange to see someone being dragged along without even being able to see what's happening?

Why are you quiet?

Qing listens quietly.

The sound of wind blowing loudly.

And up there, there's a loud snoring sound.

Hmm. They said it was a teenage sect, but the military discipline was a mess.

A commander who fails an operation should be forgiven, but a commander who fails to guard should not be forgiven, right? Wasn't it supply, not guard?

anyway.

He threw the Sapa warrior he had been dragging towards him and finished cleaning him by stepping on both his knees.

I can't see, I can't hear, I can't speak, and my arms and legs are all broken.

All I can do now was wiggle.

It's a bit of a shame that I'm deaf and can't tell you why he ended up like this.

If you said that he was a bad guy, you could have made him regret it to the bone, thinking that if he had known this would happen, he should have lived a good life.

Qing jumps up and climbs up to the gate.

"Oh my god."

There's one guy who fell asleep after laying it all down.

Even when Qing approaches, all he hears was a rattling sound.

The blue index and middle fingers sharpen the blade again.

Jang Su-hwa, the 17th-ranking official who was about to swear, saying, "F*ck, my throat was sore," was startled by the sound of a voice not coming out and opened his eyes wide.

But it was too late.

I swung my body with such force that my hair was pulling at my scalp, and then suddenly a dizzying sense of freedom from gravity enveloped my whole body.

Crack.

Jang Su-hwa's tailbone was shattered as he falls unconscious and lands on his buttocks.

Still, it's fortunate that the tailbone was not a necessary organ for the human body.

It may not seem so fortunate considering that a murderer disguised as the most beautiful woman in the world was following us.

Jang Su-hwa, who was rubbing her buttocks without realizing it, let out a whistling sound from the tingling pain coming from her tailbone.

The sudden sensation of cool metal touching my neck.

Jang Su-hwa carefully raises his head.

"Shh. Be quiet. Do you want to see over there?"

There was a riverbed that runs along the bottom.

He was seen flailing about with limbs drooping and bleeding from the chilgong.

He pretends to grab my neck with his left hand.

If a hole was made in the trachea, one cannot speak.

But the hole can be plugged.

Jang Su-hwa grabs the back of his neck.

"who……"

"Someone asked me to avenge Dan-ga-chon. Do you understand?"

"How dare you touch the river of the river-"

My throat feels sore for a moment.

It was only a slight cut to the skin, but it was enough to make Jang Su-hwa realize his situation.

"You dare?"

"no!"

It stung him again.

"Shh, didn't I tell you to be quiet?"

"Yes. Yes……"

"I have a few questions for you. Will you answer them honestly? Or would you rather be blind, deaf, and mute like me?"

"If you spare my life……"

"Hmm. Well, that's right. If something comes, something must go. If you answer correctly, I'll let you live. In return, was there a way to lie or not?"

"I won't do it."

He asks Qing to dig up some basic information.

Who are you?

Where did you come from and how many people came?

So, how many people are there in the village?

"Okay. Now, last question. Why did you kill those poor villagers?"