\chapter{A sad legend, what kind of legend was it? (13)}

It's already been two days since I came down after preparing to stay overnight on the mountain.

Tian Yuxue draws a large circle on the map.

A large circle drawn around the eastern side of Mount Lao Mountain.

"You can consider this to be the location of the Gangpaecheon guys. So this time, let's try going up from the west."

"Well, that young master has become a lord, so wouldn't he come down to find his enemy?"

Then Tian Yuxue hit Qing with a honey chestnut on his head!

Immediately after that, rub your finger joints roughly.

Unless you are a master of the current situation, you should not hit the blue one with a honey chestnut.

It's like hitting a perpetual iron, so the one who hits suffers more damage.

"What kind of brain, ugh, can't you speak a little more nicely? What's a meat fight, a meat fight?"

"But it's true……"

"Tch. It was said that words cannot be taken back once they are spoken. A word was a curse, a word was a curse. The mouth and tongue are the root of all evil. A gentleman should be careful not to speak harshly, speak three times a day, and act with sincerity. How can one be so ignorant?"

Don't criticize others without caution.

Think three times before you speak.

Please be careful with your words.

And the term '어불택발' means to talk nonsense or swear without thinking.

"Ugh. That, that's what you call a foolish person…"

A wise man keeps his mouth shut.

It means that you should not show off your knowledge carelessly.

Tian Yuxue smiles with satisfaction at that.

"Hmm. Still, you've learned a lot. To the point where you can understand everything and write a text. Anyway, speak more nicely. What's a yukjeon? A yukjeon."

"lol."

However, this was not something that a shaman like Tian Yuxue, who has a side job as a fake medicine peddler and an unscrupulous merchant, should say.

Wouldn't it be a sign of love to protect your children and disciples even if you don't protect yourself?

"Well, only the Gangpae Heavenly Lord who lost his child would be in trouble, but the rest of them would just swallow their anger and suffer the humiliation of a worthless bastard who didn't even do anything. Rather, if they can't find the Absorbing Demon Lord, they'll be the ones to vent their anger, so wouldn't they be desperately searching for him?"

If you raised your own child like that, isn't it the same as killing him?

It seems like he taught them not to work and to rape women.

"Hmm."

But Qing held back what she wanted to say.

I was just told to speak more politely, so I can't just disobey.

"It's funny. Who would deserve a thousand dollars? It's said that you can tell a parent by looking at their child. Since you failed to teach your own child, didn't you kill your own child with your own hands?"

"oh."

They say you know your teacher by looking at his students, and in the end, that student was the teacher.

In fact, Tian Yuxue was a person with a sharp tongue, so he was not good at nagging others with his words and actions.

"Anyway, let's go to Qingdo before the sun sets. The Gangpaecheon guys will have to pretend to be looking for the bad guy anyway, so it wouldn't be good if there was a commotion in the city."

So Qingdo!

There's nothing!

I've heard it's just a countryside with nothing special to see, but it really was countryside…

It's going to be just a real rural area until some country with a penchant for mustaches, slanted arms, and upside-down temple emblems colonizes it.

However, the land was fertile and the river water was clear, so it's not a remote area at all.

Saying that the water was clear was not just an empty promise, as there are not many areas in the entire Zhongyuan with water as clear as Qingdo.

Sangjanghyeon was a small city located southwest of Mount Lao.

It was a small city that can be called a tourist destination, with a well-maintained hiking trail leading to Geobong, the highest peak of Mt. Mount Lao.

However, there was no room.

Adding a little exaggeration, one of these three people passing through the city was a martial artist.

Even while the group was wandering around the city trying to find a place to stay, there were arguments like, "This guy should die!" and "Do you know who I am and are you messing with me?", but there weren't many onlookers.

It means that I've seen it so many times that I'm sick of it.

So what must it be like?

From the most luxurious guesthouses to the most run-down inns, all the rooms are full.

Somehow, I saw people sitting around a bonfire just outside the city.

However, that doesn't mean you have to stay overnight without any choice.

If you have gold and silver, renting someone else's house for a day wouldn't be that difficult.

However, it's a really poor accommodation compared to the gold and silver they give.

It was dinner time, so the restaurants and bars were packed with people, and we ended up having dinner at a cheap restaurant.

What's unusual was that the bar was packed with people, but there are plenty of seats in the tea house.

Qing strongly advocates for multi-customs.

Since the food was bad, I had to find some snacks.

Of course, in fact, half of it's just an excuse to take a teacher who enjoys tea.

And half of it's true.

I won't close my eyes until either the food or the snacks are dead.

I was given a window-side room on the second floor of the largest tea house and watched the bustling city during the off-peak season. To be exact, I only saw three rooms, excluding the blue ones.

Qing was busy eating snacks.

What's the point of going to the countryside and seeing streets full of bad guys?

That was when.

-Stop! Hey! Stop right there! Who's going to eat you?!

I thought I was getting closer when I heard a loud commotion in the distance, and someone suddenly jumped and crashed through the gaping hole in the second-floor wall.

"I'm sorry, I'm sorry! Could you please hide me for a moment!?"

He's quite polite for suddenly bringing up a topic.

"Look, we don't want to get caught up in the commotion. If we help one side, won't the other side harbor resentment?"

"Sir, that's not the case. It's absolutely not something that will cause any trouble. Please think of it as saving a life and…"

The man was desperate but polite.

In Qing's view, it wasn't exactly good karma, but it wasn't exactly bad karma either, so you could say he lived a good life for a warrior.

First of all, um? Where have you seen it?

"Um. Is it okay if I hide down here?"

"Thank you! Thank you! My Lady!"

The man, without any sense of shame, crawls under the round table.

Chen Changming and Murong Ju-hee were startled and pulled their chairs back.

This was a natural woman's reaction.

But Qing has no thoughts.

Why are you like that? You're not even wearing a skirt.

"This. Why?"

Tian Yuxue asks with a glare.

"I don't think he's a bad person, do I? And, um, and why does he look so familiar? You know that feeling where you feel like you've seen him somewhere before, like you know him after crossing a bridge?"

"Well, then."

He said that he felt like he knew me because I looked familiar.

So, I thought that Tian Yuxue would be like that too.

"You punk! Where did you go? Hey, didn't you see that guy with the cuts on him? Oh, over there? Next to him?

A rough voice can be heard outside.

While the group exchanged glances -

Someone else suddenly bursts into the room.

It's an open wall that's meant to be seen from the outside, not for people to come and go.

"Hmm? Oh, there was a guest inside."

Qing's eyes widen at him.

I know him.

"Chiljeolrangin! Aren't you Elder Yuradal?"

Although the numbers are a little off.

This was the ronin Gosu, the ronin Yura Dal, who met during the flood of Naknyeong.

"It's not a seven-day festival, but a phrase. Hmm? But do you know each other?"

In fact, it's hard to forget Qing's face once you see it.

Even the face has three.

But since they didn't recognize me, that means the makeup was effective.

Qing couldn't reveal my identity, so I told the truth.

"I'm Nanhwa's friend. By the way, this was Nanhwa's father. Come say hello."

"hello."

Chen Changming nods his head.

Yu Nan-hwa was the name of Yura Dal's daughter.

The seonnyeo-gong was currently undergoing training at the Shinnyeomun.

At that, Yura Dal's expression becomes relaxed.

"Oh? By the way, you came to find the magician too, sir?"

"Yes. I'm telling you, Nanhwa's friend, but I'm not talking about dabbling in magic or anything like that. What good was it to become strong with such vicious martial arts? So, don't get involved in this mess and leave right now. You have nothing to lose by listening to an adult."

The nagging comes out right away.

"Yes. You are right."

Tian Yuxue nodded.

Then, Yura Dal bows his head to Tian Yuxue.

Qing stares at Yuradal intently.

I wonder if the old man came to find the magician.

But Yuradal was confident.

"I'm already renowned for my mastery of the Dokmun martial arts, so why would I want to pursue magic? No, I came here to capture my son-in-law."

"Son-in-law? Nan-hwa got married? Huh, until this spring…."

"No, no. We haven't gotten married yet, huh? Last spring? Did you see the orchid in the spring? So, how was it, huh?"

"You've become a lot prettier, haven't you?"

"Yeah. Almost a complete transformation."

At that, Yura Dal's expression brightens.

"They call it Hwanmyeontalmyeon, which was similar to a nickname."

The expressions on Qing and Yura Dal's faces become subtle.

Face mask? Isn't that bullying?

Chen Changming, seeing that expression, quickly adds.

"No. She made it up herself. Nanhwa asked me to call her that."

Yura Dal nods to him.

I guess he thought it would be worth it if it was his daughter.

"Ahem. Anyway, I've got a perfect son-in-law in mind, but this kid won't listen to anyone and just run away."

"Ah."

Didn't the man clearly say that it wouldn't be a problem?

"Look at my mind. Didn't that guy with the scar on his face come here? It's called Nangyacha."

Qing tilted her head at him.

Have you heard of the Nangyacha?

"Oh, um. He went out there. He even closed the door properly."

"This brat, a ronin has his own pride, hanging around in a magic shop. You too, stop loitering around and get going quickly. I'll be going now. I apologize to the lord over there."

"What are you sorry for? Please take care."

Yura Dal opens the door to the tea room and goes out.

Outside the closed door, the voice of a man looking for a son-in-law echoes through each room for a while, then soon fades away.

"I think it's okay to come out now?"

Then, the Nangyacha Yeoktaegang crawls out.

And then he looked around slowly and-

"Are you friends of Lady Nanhwa?"

"Similar. But wouldn't a person like Gujeolrangin be a good person to serve as your father-in-law?"

"You know Miss Nanhwa, right? If only her hair wasn't long, she'd look exactly like Elder Yuradal…"

"Hey, didn't you hear what I said earlier? She's become much prettier after learning the Fairy Art."

"More than that, it's because I haven't even thought about marriage yet. I can't imagine settling down in one place."

It wasn't particularly convincing because it was said after Nanhwa's face was like a long-haired Yura Dal.

Anyway, I don't want to force someone who hates Qingdo and runs away to be with me.

"Well, if it's marriage, you have to like each other. I wouldn't get engaged after seeing my father-in-law. By the way, did you come to find the magician, Nanyacha?"

"I heard rumors and came here to check it out, but, um, the day before yesterday, I saw a certain Amukhaprap, a resident of Qinghae. If he's come all the way from Qinghae, wouldn't meddling just lead to bloodshed? So I'm thinking of leaving now."

The motto of Yeoktaekang was to join when it's appropriate and leave when it's appropriate.

This was also the reason why he was able to survive well despite being famous as a ronin.

And then Yeok Tae-gang gave his map.

"I appreciate your kindness. Please be careful."

Then he greeted Tian Yuxue and jumps over the outer railing.

I don't know why you keep going through the wall instead of the good door, but-

-You little punk! Hey, you!

-omg.

It seems like it was just a bad time.

The two people are noisily walking away, telling us to stop there again.

Then Tian Yuxue clicks his tongue.

"This doesn't look very good."

"After all, isn't it a bit much to chase after someone who doesn't want to be your son-in-law?"

Qing was beating the drum.

However, Tian Yuxue just frowned as if to say, "What are you talking about?"

"What are you talking about? Didn't he just say that he saw that lama, Amukhaprap?"

"Is he famous?"

"There are some strange people called Arab Daltaekbulshinsa. That's not the problem. The problem was that they came all the way from Qinghae to here at just the right time."

Then how did you know and come all the way across Zhongyuan?

It was never the right time to hear news by rumor or messenger.

"Was there another Jang Bo-do?"

"That's what's strange. Even if there's an original map and it's copied, how could it possibly reach that faraway Qinghae?"

"Oh. Maybe it didn't come because it touched me?"

It was a story that Qing had heard in his hometown.

What was it? Didn't they say not to make assumptions about something that's already happened?

That, a razor blade? Beckham? What do athletes have to do with razors? Of course, those people were the ones who advertised it. Oh. I want to eat tonkatsu.

But Qing learned resignation.

And no matter how much you try to figure out what the concepts of your hometown are, there was no way to confirm them, so you just end up thinking they are like that and passing them off.

Of course, there are some precious things that we can never give up on, that we can never give up on.

If you want to eat it, just make it, right?

After pounding the pork, you can coat it in breadcrumbs and fry it, right?

However, Tian Yuxue's expression did not soften.

Qing stole the Jangbodo from the Lulin general.

To be exact, what was stolen was the life of the Lulin General, and Jang Bo-do was a bonus.

And the Bingzhou Samgyeon, who had other Jangbodo, were the ones who were active on the border at the northern end of Shanxi Province.

Are you listening this time?

Even the Kunlun School Taoists moved to the eastern foot of Qinghai Lake because Kunlun Mountain was too far away, so how did the Jangbodo flow into the nearby, sparsely populated Lama Monk Sanshan?

Unless someone had planned it and spread the news.

So, Tian Yuxue had no choice but to be impressed.