\chapter{A sad legend, what kind of legend was it? (9)}

The realm that Qing thinks he has reached was the ultimate (omitted) ultimate Qing.

If others heard this, they might say, "What kind of masculine thing are you saying to gild yourself?"

But in reality, Qing proved this by hunting several Unrestrained Realm.

Nearly limitless internal energy.

The output there was also different.

The most outstanding physical abilities among primates, including strength, endurance, balance, elasticity, and flexibility.

This was arguably the most powerful of all monkeys.

And what about the intelligence that only surges when faced with a crisis?

Just like that bug, Mr. Bar.

So, Qing was qualified to speak of transcendence himself.

But what about the Master?

Of course, Tian Yuxue was a master of Hwa-jo-gyeong, or Hwa-gyeong for short.

However, it did not exceed the limits of the flower mirror, so it's not a flower mirror or a super flower mirror.

Qing already knows that there was a super-high-ranking official in the enemy camp.

In this situation, what if Kang Pae-cheon's elder and Tian Yuxue fight?

Naturally, Tian Yuxue had to fight against many opponents, and in academic terms, he ended up being beaten by many people.

So, it's inevitable that Qing's mind will be anxious.

You can't inherit the Divine Thief yet.

Qing never learned the secret of how Tian Yuxue could steal so easily every day.

Moreover, there was no such thing as a Divine Thief priest.

Tian Yuxue saw his talents well, but failed to take his nature into consideration. Even if Qing were to become a god right away, he would only be committing a great sin against the world.

Because the contemporary Divine Thief warriors will invade and say, "Hand it over now! If you hand it over, I'll take your life for free!" and become famous in the martial arts world as vicious robbers, murderers, or soul stealers.

In fact, if Tian Yuxue wanted to, he could change his profession from thief to assassin at any time.

Still, he was an assassin because he was a Confucian scholar.

An assassin was a guest who stabs.

In Zhongyuan culture, the word 'guest' refers to a person as important as a superior, so it's actually an honorific term, not a derogatory term.

This was to commemorate the righteous man Jing Ke, who attempted to assassinate Qin Shi Huang in the past but failed, saying, "The sword was too short. I should have used a long sword instead of a dagger."

A great man who committed suicide by dying for the world whether he succeeded or failed cannot be called an assassin.

So, the honorific term was assassin.

As a side note, if you had just offered Qin Shi Huang a mal of mercury, he would have eaten it and died.

He tried to stab me with a knife, but failed and ended up becoming even more vicious.

Of course, anyone who sees the real thing of mercury will think that it's a real elixir, which was the limitation of the primitive mineralogy and toxicology of the prehistoric era.

Qin Shi Huang actually died from mercury poisoning.

In any case, Tian Yuxue does not want to inflict the karma of murder on his disciple, whom he would not mind hurting even if he put it in his eye.

To Tian Yuxue, who has no interest in women and no children due to his natural talent for playing alone and being good at reversing horses, Qing was already a precious disciple, just like a daughter.

Murder was a poison that sickens the mind.

Even though he was a young disciple, he was very vicious, and in Tian Yuxue's eyes, he was very rotten and not ordinary.

So what can we do?

Even if the disciples lament, I have no choice but to ease the burden on my disciples.

So Tian Yuxue took up the dagger.

No one in their right mind would decorate their most precious tent with such extravagance.

Unless you're planning on spreading rumors around the neighborhood about an important person here.

But the Sapa guys are originally insane human beings.

Tian Yuxue headed towards the largest house without hesitation, and immediately heard an extremely ominous sound.

The sound of flesh hitting flesh.

-Can't you fucking tighten up a little? Shit, that country bumpkin bitch was fucking Yongmun Grottoes wide open. Am I fucking the air?

Tian Yuxue's eyes tremble.

Perhaps the disciple's words are right.

Is there any reason for those guys to be alive?

Apart from that, it's a perfect time to assassinate.

When a person was caught up in lust, no matter how sensitive he is, he cannot hear the sounds around him.

He said he could go in, cut off his head with one stroke, and then get out.

Tian Yuxue seeped into the house like a ghost.

However, what Tian Yuxue did not expect was Elder Il's strange castle walls.

A young man who was very absorbed in rape.

A woman who has already given up and was drooping, shedding tears of dull despair.

And the old man holding the penis while watching.

Elder Il and the Divine Thief's eyes meet.

"Your Majesty! Avoid!"

Young Master? A precious man?

Divine Thief immediately throws a powerful sword.

But the young master, who takes such great care of my safety, immediately flies away.

The stray bullet hits his shoulder.

"Kwaaak!"

The young master's scream.

Tian Yuxue tried to finish it off by kicking his body right away.

"Where!"

In an instant, Elder Il rushes in front of you and stretches out his sword.

A red strong energy that draws an afterimage in a straight line.

Tian Yuxue also spreads the faint starlight unique to Divine Thief and pushes the side of the great sword with the soft hands of Muyeong Shinsu.

In one fell swoop, Tian Yuxue and Il Jang-ro recognize each other's abilities.

'You're two steps ahead of me. This was a big deal.'

'For a Unrestrained Realm, he's a weakling!'

Tian Yuxue's face was dyed with despair, and Elder Il's spirits soar.

This was because Divine Thief was inherently weak in one-on-one, fair combat.

However, he overcomes it only through his superior intelligence and various tools of divine power, namely stolen goods.

Tian Yuxue takes hold of the dagger hanging from his wrist strap.

The young master kicked open the door and ran away, but the perverted old man standing in front of him was not in a state to be bothered by anything else.

Tian Yuxue slowly steps back, glares at the enemy, and takes a stance.

It was clear that they are trying to attack through defense.

Elder Il also cannot rush in rashly, but observes his opponent and seeks an opening.

In fact, Tian Yuxue was a swindler and a swindler, and he was just showing off.

What do you have now?

A dragon's horn, a feather, a smoke bomb, a thousand silk threads, seven daggers, a knife in a shoe…

Tian Yuxue's head spins furiously, and he immediately comes up with numerous techniques to induce certain situations and use certain tools.

Elder Il was shocked at the sight.

"That kid was being tricky," he thought, and immediately rushed forward with his sword.

The sound of weapons clashing was loud.

As Qing runs across the village, he sees a group of people running towards him.

Qing frowns without realizing it.

A naked man was running towards me, grabbing my shoulder and swinging his ugly penis.

After that, it looks like other guys followed suit.

What the heck? A naked Gubo? Why just one?

At that sight, Qing falls to her knees and lies face down on the floor.

I thought that if a villager returned late, he would behave like this.

Of course it worked.

A person's knees don't touch the ground, so if he's lying down in his mountaineer's attire with a sack tied behind his back, he's obviously a mountaineer.

The Qing's resilience for slaughter was truly astonishing.

There was a sentence written by a great writer in the hometown of Qing.

I'm on my knees to gain momentum!

The supernatural hearing and spatial perception work together to fire the sound by extending the legs at the appropriate time.

The dizzying speed brought about by human-transcendent power.

However, for a moment, time suddenly stops.

Miss, this kid was naked.

The idea was to kick the shins and give the enemy the experience of flying with the momentum of the explosion.

Of course, according to aerospace engineering, the core explosion was judged to be inadequate as a propellant.

The body would only fly halfway up before gravity would catch up and it would fall back down.

Still, the soul was certainly a noble method of soaring into that unknown universe.

But that's only when you're wearing pants.

I can't bring myself to kick the legs of a guy whose penis was dangling.

This was to preserve the dignity of my feet and shoes, the very minimum of dignity.

In a word, because it's dirty.

But humans can use tools.

Monkeys and apes are like that too.

As it happened, Qing had a disposable tool in his hand, so he quickly put the knife away and drew a cool trajectory as if he was sweeping it in the direction of the sword.

In the Ximen Qing, there was a sport where a small ball was hit with a long stick and put into a hole.

If the officials of the game had seen this move by Qing, they would have given him a standing ovation and admired it as a moving move.

Even in a five-hole stadium, it would be a distance that could be achieved in one shot, and everyone would be pushing their business cards and saying, "Let's make a new history."

Two small balls take the shape of a trampled bank, and as if that weren't enough, a crack extends from the pelvis like a giant tree branch.

Young Master, the body of Kang Pae-cheon, So Cheon-ju, and Kang Sak-mun flies backwards and crashes down unsightly.

Qing-i smacked her lips.

It was said that the feel of the sword was quite dull, as it's said that the wick [Geogaeom {Moonlight Sword (Shiho)}] was placed in a wooden scabbard.

Qing shudders at the sight of the blood and other traces left on the makeshift scabbard.

I should throw this away and make a new one.

But, it's hard to find a good stick.

Then, a spark appeared in Qing's eyes.

"The enemy of my scabbard! I cannot forgive you!"

"Master!" "Master!" "Protect the Master!"

The Sapa guys were shaking their master around and even hitting him on the cheek.

A man cannot come to his senses when his heart bursts.

Because the heart has burst.

Meanwhile, the guy who pulled out the sword suddenly blocks Qing's path.

"Who are you! How dare you trouble Kang Pae-cheon!"

A fool appears who verbally harasses Qing.

Qing doesn't give up and fights back.

"When asking for a name, it's polite to state your own first, right!? Don't you know the proper order of things, you ignorant bastard!"

"Yes! I am the first-ranking officer of the Gangpaecheon Order, the unmanned water tower commander! Reveal your identity!"

"I am the vile Unyeonyeong of the Blood Cult! Blood tax! Blood tax! Blood blood tax! Blood name was innocent! Cho Ban-yu-hyeol! From now on, this hunting ground was under the control of this blood alliance!"

"What! What the!?"

A truly unimaginable identity!

The tower commander was startled.

"What grudge does the Blood Cult have that they are targeting this fallen heaven!"

"The Blood Cult doesn't care about that! They just barged in because they were bored. Why!"

The tower commander was immediately convinced.

Now that I hear it, it's true.

This was absolutely perfect logic.

And if logic doesn't work, then using force was the strict law of the martial arts world.

"Damn it! You're the villainess of the Blood Cult! You, take care of the young master, and the rest are passable! True Dragon, open!"

Then, the Gangpaecheon warriors swarm around Qing.

Even if they showed poor military discipline, it was not wartime, it was peacetime.

The position of the Ten Great Heavenly Kings was not decided by gambling, but by the warriors of Gangpaecheon who immediately stood firm in their discipline before battle.

That was when.

"Sister!" "Young lady!"

Two women stab the flank of the passing team that was about to unfold.

Qing was moved.

How dare you jump in to help me with such a pathetic weapon!

While my eyes were drawn to the two women who seemed to get along well, Qing-i bang!

A black, mold-like aura spreads out in concentric circles in the Ximen Qing's Jin Gak.

The tower commander's pupils dilate greatly at the unimaginable acceleration.

But the unmanned truly reveals its value in times of crisis.

This was the evil gate tower leader swinging his long sword.

A line of energy that runs horizontally across the ground.

At the starting point of that stroke, the tower master suddenly realized that this move was going to be the most outstanding move he had ever made.

And when I defeat the enemy, I will surely advance to the next level.

But it's a digression!

Boo-woong, what could have been the best move just went down the drain.

There was no hope of realizing a missed attack.

This was because Qing suddenly disappeared from sight.

And that blue was now on top of your head.

It was rare for a drone to jump.

The reason is, first of all, that in the air, it's difficult to freely control one's body, let alone find one's direction.

Because it becomes extremely vulnerable when floating.

However, the advantage of using that blind spot was that it can easily get out of sight.

Qing raises his sword and strikes the rising energy in a straight line.

The water tower commander, who belatedly noticed the momentum, lifts the sword with his hand.

The second reason why unmanned vehicles do not jump.

The power of the unmanned comes from the earth.

The power of falling from the air depends solely on mass unless it's a special martial art, so its limitations are clear and the destructive power of the attack was poor.

Bang!

Yet, the sheer force of the swing causes the tower commander's knees to bend.

If the knees hadn't bent, the blue would have bounced back due to the difference in mass.

However, since his knees were bent and the impact was absorbed, Qing didn't bounce off and landed quietly, hitting the shin of the tower commander who had already lost his posture!

The tip of Qing's foot struck the shin bone of the water tower commander.

"Ah!"

"Be quiet!"

The upright fist of the blue dragon, the moonlight sword held in it, the weight under the handle sticking out long from below the fist, and it's embedded in the shoulder of the tower commander.

That was a very accurate expression.

The weight penetrates the shoulder blade and sinks into it.

What kind of thing was a weight?

It was thicker than the handle to prevent your hand from slipping out of the handle, and the bottom was flat to add strength when stabbing.

How much force would it take for such an object to penetrate a human body?

What was certain was that at least the strongest human being can do it.