\chapter{A sad legend, what kind of legend was it? (1)}

The raindrops that had been falling one by one started to pour down, so I thought it would rain heavily, but just as we were finishing our meal, oh my… …! It started to pour down really hard.

The sound of rain heard in a place that doesn't get wet creates a sense of comfort that soothes people's nerves.

Chen Changming, who was tired from hiking all day, dozed off after eating, but was overcome by the sound of rain and finally collapsed.

He gets up from his seat.

"Where are you going?"

"I'm going to boil some water. Please wait a moment. I'll bring you some hot water."

"Ahem. It's raining, why are you doing that? I was just going to go out and get some rain."

Despite what he said, Tian Yuxue's lips loosened.

I am used to staying overnight in Qingna or Cheonyuhak.

But Qing doesn't like soaking in hot water or anything, and if it's not a hassle, then it's probably a waste of time washing up anyway since the sand from the overnight stay was the same.

On the contrary, Tian Yuxue was the type to take care of cleanliness even when staying overnight.

Since Qing knows the teacher's tastes, what can he do? The disciple must take care of it.

"That's why I'm going to get some rain. If I get some rain on the dorongi, will the smell go away? Will it wash away a bit?"

"It's less. Human. It's more."

As Qing opened the door, a refreshing sound poured out all at once, filling the room.

Qing hesitates for a moment, then quickly leaps out of the eaves.

It's a torrential downpour that feels like you're being hit by raindrops rather than rain itself.

When I'm getting rained on like this, I strangely think of the other world before I left.

Why? Because you don't get rained on over there?

Oh my, it's so refreshing. Hmm, I'm craving green onion pancakes and seafood pancakes. Dip them in spicy soy sauce with finely chopped chili peppers and eat them. Wow.

This was what Qing, who just came out from eating, thinks.

Qing first heads towards the center of the village.

"Ugh……"

"Hey. It's tough, it's tough."

Amazingly, all six of them were alive!

Judging from the opinion of the medical woman Qing, not the martial artist Qing, there was no possibility of revival.

But in the opinion of the martial artist Qing, not the female doctor Qing, those guys are good-looking.

Look, aren't the corpses of the innocent villagers piled up in the vacant lot also smiling brightly?

The corners of your mouth are hanging down to your ears.

But how can a corpse laugh?

Qing rubs her eyes.

But you didn't see things the wrong way.

But wouldn't all the slaughtered villagers, all those countless corpses, turn their heads and look at the evil villains swarming like insects below them, with their wide, gaping eye sockets and evil smiles?

There were even many heads that were bent at impossible angles, so since they were dead once, they can't die twice, so they just turn them without paying attention to their neck bones and muscles?

"Ugh, ugh……"

Even through the gag still in his mouth, the groans of pain could be heard very clearly even amidst the loud sound of the rain.

With clothes clinging to his skin, how painful it must be for the raindrops to fall hard and hit his melted body.

It would be better to kill him with one stroke of a sword.

"Does that even make sense? I'll just keep suffering even after I die. Everyone's cheering me on so quickly. When I get to the afterlife, oh."

Qing snaps her fingers.

"There's a saying that when you go to the afterlife, the innocent people you killed will come out to greet you, swords in hand. All the guilty will be condemned to hell, so only the innocent will come out for revenge. Hmm, isn't that a good thing? This was how the afterlife should be."

Qing, whose mood suddenly improved, hums a tune and leaves.

Go into an empty house and pick up an empty pot. Two here, two from the house next door, and the house next to that. Hmm, the dishes here aren't washed, pass.

There was a pot in the house I am staying in now.

But I didn't want to bother with the dishes, so I went out to look for a clean pot to boil water in, to check on the state of the burning human blankets.

After I offered the pot of boiled water to the teacher, the sun had completely set, and since it was already pouring rain, it was pitch dark and I couldn't see anything.

"Okay, get some rest. I'll sleep in the room next door with Jangmyeong and I'll greet you in the morning."

It was not necessary to be married to the teacher.

I just gave you hot water, so you should wash it.

"Okay. Tomorrow, as soon as the sun rises, I'll be heading straight back to Immu-hyeon, so don't stay up for nothing and go to bed early."

"That's right. Do you have any incense (soap)?"

"Huh. Have you ever seen me walk around without incense? You're the one who doesn't wash, not me."

"I'm just going to wash up in the front yard."

"Why are you saying you're going to shower all of this time? Are you afraid I'll spy on you? Yeah, right? You're going to shower in the rain? Outside?"

"You poured a lot of it? It foamed up and then washed it all off—"

"What the heck? A girl so fearless. Even if it's dark outside."

"Hey, it doesn't matter if I lose and no one comes looking for me, and I can't see an inch ahead of me."

"Tch, Arthur, Arthur. Is this being bold, or, um, ha, I don't know what to say. There's a limit to being rough around the edges. How could a girl, not even a man, strip naked and go outside?"

If Ximen Surin had heard this, it would have caused her great distress.

So, does that mean that men can take off all their clothes and wash their bodies in the running rain, but women can't?

Well, of course not. That's true.

But if it's a man, it's okay, but if it's a woman, it's not okay.

But what was this worthless disciple doing? Even if it's dark at night, how can a woman expose her body so clearly? Oh my god.

So in conclusion, it will end up being a huge blow to the disciple.

Unfortunately, Ximen Surin was not here.

Tian Yuxue has no desire to argue with his disciple over such a masculine topic.

Qing had experience washing in rainwater from his past military experience.

So, I think it's okay since no one will see it anyway, right?

In Zhongyuan, there was no acid rain and clean water falls. Isn't it cleaner than the Zhongyuan-style bathing where you have to fetch water and wash?

So, the miraculous scene of the most powerful woman in Zhongyuan, the most beautiful woman in the world, running out and enjoying a bath in the rain, ends without anyone seeing it.

The sky was covered with clouds and the ground was flooded, so it could be said that one of the most beautiful scenes in the human world passed by without anyone noticing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing wakes up at the crack of dawn.

As I lay there last night, I thought about it and realized I should get rid of the burnt corpses so they're not visible.

I think it might be a bit weird for the elderly and children to see.

As if it wasn't enough, it was still raining all night, and the sky was pitch black, but the sun was still rising near the ridge.

With Qing's superhuman vision, the outlines of objects can be barely distinguished.

As I went out to the square wearing my blanket, I saw that the guys who had lost their blankets in the fire were lying in the mud, their breath gone.

Hmm. I wish he was still alive, but maybe it rained overnight and he died sooner?

Qing roughly grabs his ankle and throws him over the cypress tree wall.

There was no need to ask or hide it, just put it away so that it's not visible on the way out.

And looking at the pile of corpses of the villagers, Qing tilts his head.

What? Weren't you smiling yesterday?

Or did he return to his original state after seeing his enemy die and being satisfied?

Qing felt a little regretful.

Since you're already laughing, laugh a little more.

I could have shown it to Master and Changming and said, "Look at this. These people are smiling because they have let go of some of their resentment."

But regret was regret, and a dead person was a dead person.

It's sad that he died, so I can't criticize him for not smiling.

Qing respectfully clasps his hands together and recites the sacrificial rites.

Then, after greeting each other in the morning, we light a fire and prepare breakfast with Jangmyeong, who has been sleeping soundly since early evening.

To be exact, Changming'er was just pacing around here and there, doing nothing, while Qing was actually preparing breakfast alone.

But this was originally the youngest's job.

Something that just hangs around and doesn't do anything, but sends a signal that it wants to help.

Of course, if the youngest sloppily tries to do something, it will end up ruining what was already working, so it's the youngest's job to just watch from the sidelines and understand how things work out.

Still, taking on an attitude that suggests you want to help was just a way to be loved.

"Why was the table the same as yesterday? Or was it even worse than yesterday? At least they served egg porridge last night?"

The central table was divided into dishes and banchan, or in other words, dishes and meals (main dishes and side dishes) in the Qing homeland style.

And there are levels of food, so rice was on the same level as white porridge, and to be on the same level as egg porridge, it should be the first level of eggs, that's, fried rice with eggs, right?

"Hey, what kind of porridge are you having in the morning? And what ingredients do you need to make it?"

"What? What does breakfast have to do with porridge?"

"Hey, people need to eat to gain strength."

"What? What does food have to do with strength?"

This was something that Zhongyuan people absolutely cannot understand.

But to Qing, it's common sense.

What's dead in the morning?

When you're sick, or at the end of a soup.

"Isn't this the same hodgepodge as yesterday?"

Well, I guess that's the limit of pseudo-study.

Why, even in the hometown of Qing, isn't there someone who can make an unidentified mixed stew or fried rice with leftover food using what they have at home?

That's about the extent of Qing's skills.

However, if you know what to put in and taste it, you can tell the difference between what was delicious and what was not, and since you are good at adjusting the seasoning, even if you make it roughly, you can make something edible.

"There's a chicken coop outside. Why don't you catch a few chickens and let them simmer there?"

Qing laughs at him.

"Because I don't know how to catch a chicken."

"What? Why?"

"Uh, do I usually have to know?"

Oh my, even Tian Yuxue was like that.

Well, the disciple was a martial artist, so wouldn't it be normal for him to not know?

"Ahem, no, you're so good at staying out late. You eat berries, pick mushrooms, and dig up wild vegetables, so I naturally assumed you knew how to hunt."

"I hunt, but I don't know how to prepare it. If you just grill it, it's tough and chewy. Plus, the outside was burnt and the inside was raw."

"Of course it's, since you didn't drain the blood and fat. Oh, you should've told me sooner. I'll teach you when we go to Mount Lao."

"Oh, so you know how to do it, Master?"

"I learned it as a hobby."

"Then, why don't you teach me how to slaughter a chicken now? I have some cornstarch in the kitchen. It'll be delicious when fried."

"No, when are you going to slaughter the chicken? We'll be back in the morning anyway, so we can just go to a restaurant and have a big meal for lunch."

"Even if that's not the case, it would be good to learn it when there are stray chickens."

He was a very passionate learner when it comes to eating.

If he had been this sincere about martial arts, he might have reached the next level by now.

It was a rewarding learning experience with this unexpected chicken catching practice.

It was a moment when Qing, who was always serious about eating, learned how to slaughter birds.

Yay. Now you can catch and eat birds.

I've found all the birds. Just wait.

Could it be a coincidence that at this moment, all the mountain birds in Zhongyuan flinched?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

They traced their trails back to Jimo.

In fact, there was a reason why they returned to Jimo instead of heading to Mount Lao.

"If you're going to cause trouble in the mountains, you should at least keep your identity completely hidden. How can you possibly bear that grudge?"

"Oh. Then?"

"I need to change my face a bit. Yeah, you should learn it while you're at it. It's not that difficult of a skill. It's not that hard to change someone's appearance, after all."

So, after unpacking and leaving, I walked around the market and shopped for various items.

Glue, starch, and beeswax and honey for sewing tools? Why honey?

There are tendons, fascia, intestines, all kinds of grain flour, etc.

It was a miscellaneous shopping cart list with no clear purpose.

And then, back to the beginning, we started a full-fledged makeup class.

\vfill
\begin{lstlisting}
	The chapter title is a reference to another line in K-drama Iris (아이리스)
\end{lstlisting}