\chapter{Bound Together (10)}

The guard at the main gate, who was supposed to guide us to our seats, walked across the huge upper manor with his chest puffed out in pride.

It would have been like a triumphant general returning from defeating an impossible enemy by raising just one flag.

Since the person was carrying a god, his shoulders naturally widen, his spine straightens, and his steps were confident, as if he was trampling the ground.

Of course, I was impressed by the bold steps of the person who didn't know the circumstances.

What kind of place was that heading to?

In the garden, you continue to go deeper and deeper, passing through gate after gate, and soon you pass through a large gate and a wide courtyard spreads out before you.

On the front, a plaque with bold letters tells the name of the building.

Seonghwa Sun Palace.

Below it, a string of inscriptions hangs, conveying two lines of text.

The universe's only bright and bright source of light, the great and wise man's spirit, the Stream of the Universe

The Supreme Dignity of the Three Thousand Worlds, the Light of the New World

It looks a little shaky to Qing.

Sun Palace? Sun Palace? Is that the right name?

"What was this place? Is this some kind of shrine?"

"It's not a new temple, it's, um, uh, a guest house."

"Here we are? Anyone who sees this building can tell it's dedicated to someone."

It's the new party.

But it was also true that the person I was serving at the shrine was right next to me right now.

The clerk quickly makes an excuse.

"Ahem, that, that, that's what it's used for, but only when there's no one staying inside. Now that someone has arrived, it's considered a guest room……."

"Huh? A guest house and a shrine? They only serve the ritual when there were no guests? Does that make sense?"

Qing asks in bewilderment.

Well, isn't that what they mean when there were no guests in a room at a guesthouse, they use it as a church sanctuary or a temple hall?

In the first place, a shrine was a place where a god was enshrined, so isn't it a space where the emperor was always present and where you have to be careful about your conduct even when passing by?

Do you usually invite guests to places like that?

No, since you said the guest comes first, does that mean you only invite me when there were no guests?

"Oh, well, it would be a shame to leave this well-built guest house unused, even if it saves space."

"No, that Xuega guy was saving money in strange places. Well, he's not really the type to practice religion. But what's he doing, a local guy? Oh no."

Qing quickly changed his words.

Even in Zhongyuan, there were gods that were particularly followed in the region, and usually one of the more famous ones would become very popular.

Usually, it was one of the Taoist immortals or Buddhist Buddhas, but sometimes, there were cases where a strange god that has never been heard of or a twisted mixture of several gods takes its place.

Others might simply say that it was a local god, but it was something that should never be said in front of a believer.

"Who did you invite? I hope he's not going to commit any blasphemies or anything."

It was the voice of that strange god, the master of the Sun Palace, asking.

"Absolutely not. It's just being used for its original purpose, so it's only natural that you, Miss, would stay here."

The answer was extremely decisive.

Because it was an attitude of speaking facts without even a single doubt, Qing felt a little relieved in that regard.

"Well then, rest in peace."

"Hmm? What about the room?"

"Huh? A room?"

For a moment the two faced each other.

The owner of the Seonghwa Taeyang Palace was the Heavenly Demon King.

So the guidance of the main gate guard ended the moment we entered the courtyard of this magnificent shrine.

But from Qing's perspective, it's a bit questionable whether this was a guest house, a guest house, but anyway, if they have a huge mansion that's like a palace and don't even give you a room, what can you do?

"Ah! That! Yes! Since there were no other guests right now, you may use any room you wish."

"Ah. Yes."

It's a bit burdensome, but I'm also happy because I paid the rent.

The group went into the Seonghwa Taeyang Palace to unpack.

And wouldn't the main gate guard follow him as if it were a natural part of the group?

What the heck? I thought he was the main gate guard, but was this person a customer too?

Didn't you say that no one stays alone? And just now?

"Is it okay for you, Musa, to keep the main gate empty?"

"It's okay. Isn't the task of attending to the young lady's needs ten thousand times more important than the main gate and such?"

Qing understood it as I wished.

It seems like he wants to stay put and rest under the pretext of welcoming guests rather than guarding the main gate.

Of course, that would be the case.

Xuega Sanghoe, was this okay?

"Oh, Miss, this room was the best. I would really appreciate it if you could use this room."

"Huh."

The direction that the main gate guard politely pointed with both hands was the large door at the end of the hallway.

In the architectural style of Zhongyuan, wouldn't it be the core and most precious room of the building?

When Qing opened the door, um, what was this?

Is this a room or a training hall?

The bed that was set up against the front wall alone was as big as the entire comfortable and bleak moat of Qing Dynasty.

And yet, there was so much space left that the room felt desolate and dreary.

Even though he was a luxurious traveler who only stayed in the best rooms in the best guesthouses in each neighborhood, he was a little discouraged.

They call it the Seonghwa Sun Palace, isn't this a real palace?

Even if the bed was big, it's good.

Why on earth were we wasting this vast space like this?

Of course, if fifty million believers were to come face to face with the Supreme Being and pay their respects, there would have to be a space where they could all come in and bow down.

Because it was the bedroom where the master of the Seonghwa Sun Palace stays and also the audience room.

"Oh, right. Is it Qingcheonru? Can I eat there without a reservation? If not, was there a good restaurant? I'm thinking of having an early dinner and getting some rest."

"Oh, you mean the market! I'll arrange for you right away! Please wait a moment!"

"Huh? Wait a minute-"

Without even being able to catch him, the guard at the main gate, with a solemn expression on his face, suddenly performed a light technique and disappeared.

Even for Qing's discerning eye, who was already recognized by many as the best in the world, his studies were not ordinary.

No, just go and eat.

Why did you go first and even make an arrest?

Qing puts her embarrassed hand back where it belonged, on Ciyu's back.

Then, Peng Daesan asks with a weary look in his eyes.

"I thought it was strange from the start. What on earth did you do to deserve this treatment?"

"The founder's friend and also the co-founder's daughter-in-law? Why, there's this old man. He's a bit senile and thinks I'm his daughter. Well, it's a strange story, so we're just hanging out."

"Hmm. Even so, isn't that a bit excessive? They say courtesy was proportional."

"It's true that the Xuega Sanghoe members were somewhat like that……"

However, it was a blue that was strong in malice but weak in kindness, and it melts away very easily.

So, something seems a bit fishy, but I guess it's just like that.

The people of Lanzhou claim that Lanzhou was a city located at the source of the Yellow River.

In fact, the starting point of the Yellow River was Mount Arabdal in Qinghai region, the mountain where Qing Dynasty wreaked havoc with their tactics.

And since there were villages, big and small, along the stream, the Lanzhou people's claim was fatally flawed.

However, since this was a saying that has been passed down since the time when Qinghae was not part of Zhongyuan, we may be able to give it some leeway.

And in the middle of Lanzhou City, there was a huge pavilion that overlooks the winding Yellow River both upstream and downstream.

It was Qingcheonru.

It was originally called Hwangha Tower.

This was how the people of Zhongyuan name themselves.

However, the name of the pavilion changed a few years ago when its owner changed, so the people of Lanzhou were still not happy about the new name.

In the Yellow River Tower, you mean Qing Sky, without the Yellow River?

To begin with, the water of the Yellow River isn't even blue?

Even though the sky was so blue this week.

But if the building owner says he will do whatever he wants with his building, it was useless for the residents to complain.

Of course, there were attempts by local leaders to block it by mobilizing all their connections.

However, Zhongyuan' network was a very rational system, a relationship system, that gave higher ranks to those who provided greater benefits.

So the difficulties faced by the officials due to the barrage of petitions were replaced by greater gold.

Are you dissatisfied, poor people?

So, it must have been a very curious thing for the people of Lanzhou.

Who on earth owns Qingcheonru?

It was also unknown why the good Yellow River was given the common name of 'Qing'cheonru.

Just enough wealth to swallow up a city's representative building and silence its officials.

All you can know was that if you dare to cause trouble, you will be surrounded by skilled fighters from somewhere.

Anyway.

Qingcheonru was the best restaurant in Lanzhou.

And today's Qingcheonru was the worst.

"We're closed for business today. We'll refund your money, so please return as quickly as possible."

"Huh? What was it?"

"Please finish your meal immediately and return. I will refund you double the amount."

It was happening on the top floor of Qingcheonru.

"What the heck, do you know who I am?"

"I'm sorry. Please cooperate."

In any pavilion, the top floor was originally a place where only the most precious guests sit.

If you were told to leave right away, would you go out quietly?

Of course, I'll go out quietly.

"Then there's nothing we can do. Come on, let's go."

"There must be some urgent matter that has brought you here. Isn't that right?"

"Yeah. Okay. That's right."

Is it because they come from a wealthy and noble family that they show that much generosity?

Or was it because the famous Qingcheonru guards, martial arts masters, come up one after another and fiddle with their sword hilts?

The truth was that no one will ever know.

As soon as the guests leave, the experts all take their seats.

Then, each of them takes a table and places a weapon that was like a lifeline to an unmanned vehicle.

It's a childish position that you wouldn't even be able to mourn for.

In this way, the owner of the table was decided around a seat by the window.

Some of the higher-ups would give a hint and tell me to get out of the way.

Some people pretend not to notice even though their eyes were trembling.

Then, each person grabs the table and starts clearing it with their own hands.

Well, there's nothing we can do about it.

A golden opportunity to dine with the most honorable of beings!

So, almost all of the existing customers disappear, and new people take their place.

Of course, there were also existing customers who stayed put, and they were believers who had a dreamlike opportunity to come out to eat.

So, every seat except one was occupied, and dishes of slightly different appearances fill the table.

Of course, the kitchen of Qingcheonru was preparing meals for the nobles, so the dishes were bought from a nearby restaurant.

Then a strange scene unfolds.

New guests were rummaging through the plates, picking at the food, and taking away the food, but no one was putting it in their mouths.

How much time has passed like that?

It was after all the dishes that had been thrown around for no reason had gone cold.

Yet, a strange heat spreads across the top of Qingcheonru.

And finally.

A group of people steps onto the top floor.

The room becomes quiet for a moment.

It was the moment when the woman holding the child tilted her head.

"Ahem."

Someone cleared their throat loudly.

Then, those who suddenly came to their senses began to have extremely awkward conversations, saying things like, "Oh, did you hear that story? I didn't hear it." "That's right. I heard it. I heard it well." "I see. That's what happened. And that's true."

Well, I don't want to burden you, but I also want to eat together.

Should I say that I am very eager to eat a meal together?

If someone in the future were to see this, they might get angry and say, 'Religion was indeed the opium of the people'.