\chapter{Bound Together (9)}

The distance between Xinying, the capital of Qinghai, and Lanzhou, the capital of Gansu, was only a mere four hundred li.

For the people of Zhongyuan, who were masters of walking (and of course, this was true for anyone in this day and age), it was a very short distance.

However, the difference in height was quite drastic, with Xinying City, located on a plateau, being 250 zhang higher.

By Qing's hometown standards, this was equivalent to a three hundred-story high-rise building.

That means the road to Lanzhou was a three hundred story downhill road.

On the contrary, the uphill road to Xinying would be a difficult and rough road even for a walker, but the opposite was easy.

Going downhill might not be very good for your knees, but it was comfortable for your body.

The human body originally had a fatal flaw in accepting harmful things as comfortable.

So, Lanzhou!

As one of the oldest ancient cities in Zhongyuan with a history of 1,700 years, when you think of Lanzhou, its bizarre shape was the first thing that comes to mind.

Lanzhou was long.

In contrast to Gansu Province, which was elongated from north to south, Lanzhou was a city that stretches like a snake from east to west along the upper reaches of the Yellow River.

The reason was because of the mountain.

Gansu Province was long from north to south because of the mountain ranges on the left and right, and Lanzhou has a shape that was long from left to right because of the high mountains on the north and south.

Actually, Qing has been here once before.

But at that time, I was truly a victim of kidnapping and a captive.

Thanks to that, I didn't get to see a single sight of the tourist attractions.

Hmm. Now that I think about it, I'm getting pissed.

You cheap bastard, you little shit, you should've just gouged out both of his eyes.

Anyway, Lanzhou.

The weather was already different, having just come down from a cold place, and the gentle, warm late winter sunlight was pouring down.

Ciyu, who had settled down in Qing's arms, had an awkward attitude, half curious and half afraid.

It was my first time in a foreign land, and I was so curious that my eyes were rolling around.

But I'm still afraid and reluctant to be around a lot of people.

So, whenever someone makes eye contact, he quickly buries his head in the back of Qing's neck.

Anyway, it was Ciyu who was sticking to Qing.

Even though there was a person named Jian Buxi, who was the best in the world, no, the best in the past and present, among the group.

Go means old and Geum means present, so Gogeum only combines the past and present.

Even in the future, there will never be a pedestal superior to the Kianpohui, so the expression "best of all time" was an understatement. It was the universe's strongest pedestal, boasting the greatest ride quality ever, unparalleled in the past and present.

It was Ciyu who refused the special support of Gyeonpo-hee and crawled into Qing's arms.

However, since the cushioning material was large and soft, and the original strength was good, it won't be particularly uncomfortable.

Qing asked, patting Ciyu on the back.

"San? What's famous here?"

Qing asks Peng Daesan as if it were a given.

Well, I guess I knew it well.

Look, even now, the fact that he opens his mouth as if it were a given was clearly an attempt to be the smartest person among those who were not classified as intellectuals.

"For now, there's the White Pagoda Mountain-"

"Oh my. Why are you doing this? San, is this how it's supposed to be?"

Qing cuts off Paengdaesan's speech.

At that, Peng Daesan snorts and corrects his words.

"First of all, there's beef noodles. They say Lanzhou beef noodles were the original version of Zhongyuan beef noodles. Of course, since that's what people in Gansu Province say, I'm not sure if it's entirely believable."

"Right. Um. Um. Then. And?"

Only then does Qing nod her head in satisfaction.

If you ask what was famous, of course I should start with the food. What was Baektap? What does it matter if it was Baektap or a white tower?

"There were sheepskin, Hwangmin Yangyuk, Unae Gyedan Yojo, Chomyeonpyeon, Sampotae, Hoeduja, Yangjapswaetang, and Mimyeonheultap."

When it comes to Zhongyuan cuisine, you can usually tell what it was just by its name.

For example, Hwangmin refers to a stew that was boiled until soft and mushy, so if you say Hwangmin Yangyuk, it means stewed lamb.

The same principle also applied to the sudden sparkle in Xue-i's eyes and gulp near the Yangjapsae-tang.

Just hearing the word "sulli-ri-tang" automatically makes her ears perk up and her saliva drip.

It was a thought that brought to mind the dog of the yet-to-be-born Westerner, Mr. Pa Mo.

Since Xue-i-ri's conditioned reflex was formed before that dog's, shouldn't it be a theory like Xue-gun-yeong of Tangguk, not Mr. Pa's dog?

Of course, there was a much more important question than whether the dog came first or the sheep.

"Why are they all noodles?"

If you look closely, there were already four noodle dishes: Uyukmyeon, Yangpi, Chomyeonpyeon, and Myeonheultap.

Qing didn't know, but in fact, when it comes to braised lamb, noodles were boiled in broth and served together, so there were five, not four.

"In the north, it was customary to eat noodles."

"No, I think it's good. Hmm. First, let's eat a lot of rice. San, do you know any good restaurants?"

Pang Dae-san was about to spit out the names of several famous restaurants he had heard about in exchange for coins from wandering storytellers.

"Oh, Xiao-mei, I know. There's a place called Clear Sky Inn. It's delicious there."

"Yi-mey? Have you been here before?"

"Yeah. But I don't know anything outside of the area around the store."

"Store?"

"Yeah. Xuega Sanghoe."

It was a name that popped up out of nowhere.

A familiar name heard in an unfamiliar place.

"Huh? Xuega Sanghoe has advanced to Lanzhou?"

"Yeah. The building is really big too?"

So, Lanzhou, Xuega Sanghoe.

Even if the world developed at the speed of light, a small city was still a small city, and even if it was a city in a remote area that has fallen into disrepair, it cannot be compared in scale with a large city representing a single province.

And the owner of the Xuega Sanghoe, which was well-established in these big cities, is, um. What was this?

The signboard with the four characters of Xuega Sanghoe written on it was about a page long on both sides, so how big would the main gate be with a structure like that attached to it?

In fact, it was a natural thing.

Lanzhou was the largest transit city on the Silk Road, and was located on the passage connecting Cheonsanshinshi of Cheonmasinkyo and Zhongyuan.

If they took control of Lanzhou, the road to Qinghai in the east, Shaanxi in the west, Sichuan in the south, and Zhongyuan would be wide open, so wouldn't they have put all their efforts into taking control of that commercial area?

Of course, Qing doesn't know such circumstances.

Xue-i-ri's eyes tremble slightly as she stares blankly up at the palace-like main gate.

It was a surprise to those who realized too late that Xue Ga-nom, that is, Uncle Yusa, was richer than they had thought, no, beyond their imagination.

Qing was a little surprised.

I wasn't very surprised.

I already know the skills of that hasty and incompetent Xue Ga-nom, so it was already a given that he would be a great success.

Is it just new or unfamiliar?

It's like I went to a tribal village in the middle of a primeval forest and found a fastfood franchise has moved in.

With this level of success, I think we should expand the scope of the first-class intelligence a bit.

Two grades of provincial government? No, Shaanxi Province was actually a thief who stole the heart of that bastard who was a branch office, so he should be given three grades of provincial government.

So, was this roughly the intellectual who represents the central region?

What was the most intelligent thing that Zhongyuan can do?

One fifth of the best in Zhongyuan Province?

Either way, the it doesn't roll of the tongue well.

While Qing was seriously contemplating the title of Xue Ga-nom, Jian Buxi walked in with a confident gait and spoke to the guard at the main gate.

"This is thebranch office of the Daeseolga Merchant Association. What brings you here? Do you have an appointment?"

"Huh? Ung."

Ung means no.

Even if you were not a Jian Buxi, it was an expression that a woman can use, but a man cannot.

Because if a man said it, he might get beaten up.

Anyway, the guard looked like he was about to ask what kind of woman she was, as if she was full of coquetry and negativity.

To this, Jian Buxi adds a word.

"I'm Jian Buxi."

It was a very arrogant expression.

Isn't this an attitude that seems to assume that you should naturally know who I am?

That's why the main gate guard was momentarily dumbfounded and thought, 'What was this? Jian Buxi? Is this an expression used by young people these days?' Then, suddenly, the name came to mind.

"Huh. Do you, by any chance, have an identification?"

"Yeah. Okay, here. Oh, and your nephew? Is he here?"

"He headed to the Holy Land."

"It's a shame. That's right, I came with my Sworn Sister."

"Huh!"

The main gate guard's eyes open wide.

Jian Buxi, the Guardian of the Heavenly Demon Cult and the Sworn Sister of the noble Heavenly Demon.

And that Guardian had only one sworn sister, so what if she said she came with her?

"Now, if you just wait a moment, hey, I'll send a message right now, no, no! I'll get it, I'll get it, ugh!"

The flustered guard at the main gate stopped breathing.

Well, a woman carrying a child approached. And she was carrying a very large sword, which looked ridiculous.

"Hmm? Are you okay?"

"That, your honorable… Young Lady. Is it really you?"

'If you happen to meet the Supreme Being, do not say things like "Supreme Being," "Heavenly Demon," or "Highest Dignity."'

Remembering such thorough training, the guard chose what to say and finally found the right words.

"Hmm? Have we met before? Have you been to Zigui by any chance? That Xuega guy, hey. This won't do. Overseas. Not overseas, but it's useless to be sent this far away."

It was the moment when the main gate guard was certain.

He is! My light! My master!

"No, it's not! I've heard so much about you, my Lady! It's an honor to meet you, an honor of three lifetimes, no, an infinite honor of ten thousand lifetimes!"

"No, it will be endless……!"

"I wonder if it would be impertinent to ask if you would allow me the honor of welcoming you, my Lady?"

"sure."

"Oh, how merciful! I will treasure this Jihanru, this glorious moment, as a blessing for the rest of my life! This way, this way!"

The expression on the face of the man following behind was bitter.

Looking at the enormous hospitality shown to the guests, which makes it hard to tell whether it was a formality or a sincere gesture, it seems that this was indeed a Xuega Sanghoe.

No, but how on earth do you train your employees to have such an attitude?

Is Xue Ga-nom the culprit or was Grandpa the culprit?

A huge bomb was dropped on the Lanzhou Xuega Sanghoe branch, also known as the Lanzhou Temple of the Heavenly Demon Sect.

She-Who-Should-Not-Be-Named, had descended!

To the followers, Qing was a real, sage god.

There he was a great conqueror who was carrying out the conquest of Zhongyuan in real time, a conquest that had been stained with blood and failure throughout the history of the religion.

The merciful Master of our 50 million followers (estimated to be of the Cheonmasingyo) who has advanced into the impregnable Zhongyuan without shedding a single drop of blood and taught us how to live a human life, has visited us and provided us with the faithful happiness we now enjoy.

For the followers who had experienced the wild and powerful world of the past Cheonmasinshi, their current life was like a dream, a supreme happiness that made them afraid to fall asleep.

Among them, the staff of Xuega Sanghoe were especially considered to be of very high status among the followers, as they had been devout and had proven their fanatical faith since the past.

in result.

Currently, the losses of Xuega Sanghoe were increasing rapidly.

Well, since the Heavenly Demon Lord has descended upon the main building right now, how can things be handled?

Those inside were busy thinking about how they could make natural contact and offer tribute.

Those working outside have no control over their work, so the work of Xuega Sanghoe, which used to run like a sophisticated machine, starts to creak and mistakes, big and small, start to appear here and there.

Of course, no one blamed him for that.

This was the difference between business and religion.

Money was good if you make it, but if not, that's it.

How can you endure it when Heavenly Demon herself has come down to you?