\chapter{Bound Together (4)}

The three Profound Realm masters decided to stay at Kunlun Sect and monitor the movements of the general.

Since the Xizang's greatest master has been defeated and has become involved with the Blood Cult, the Potala Palace won't be making any moves for a while, but you never know what will happen in this world.

Even Qing knew how shameless those brazen bastards could become.

Even without the ability to see through people and slowly become close to them, wouldn't the masters who roamed the martial arts world have experienced this situation countless times?

They just put a steel plate on his face and locked him up as a useless person, the innocent Seo Jang-jeil, under the false accusation that the people of Jungwon were members of the Blood Cult.

If you insist that it was worse than death, that's it.

Rather, it could fan anger and create an excuse to attack immediately.

Of course, the chief wouldn't do that.

Isn't conspiracy ultimately a matter of profit?

Take control of Qinghae martial arts world, establish a faction, and disguise the best martial artists to move in.

The plan to recover the land of Qinghae at once once enough power was gathered was testified by Runlin, the chief priest of the Blood Thunder Temple.

However, even though Seo Jang-jeil borrowed the power of the Blood Cult, he was defeated without any strength.

Greedy people don't move when the risk outweighs the gain, so I had no choice but to trust him.

I was planning to stop by the Wulin Alliance for a bit on my way back to Nan-Gongdaero to report the situation, so I left the Giant Pagoda Emperor in Shaolin on the way.

It was a bit disappointing news for Qing.

If I had stopped by on my way back to the Divine Maiden Sect and taken her away, she could have harassed me for a long time.

Depending on the situation, I plan to quietly cut off all the fingers of the Emperor or the Heavenly King.

Living in a prison cell, I realized that if someone couldn't even speak, they would likely go crazy. If they cut off their fingers, wouldn't they be able to make it so that they couldn't even write?

But then I think about it.

If you don't have a right hand, you can use your left hand. If you don't have both hands, you can use your toes. If you don't have your toes, you can use your two stubby hands.

So what?

One can only hope that the prisoners of Shaolin Temple's Penitentiary will diligently torment the stiff, mute barbarian.

Rather than that.

"Hmm."

Qing's footsteps become slower and slower.

Just around the corner, the Blood Thunder Demon's temporary lodging appears.

\textit{Rather than that, the child, uh-huh.}

\textit{I didn't say anything wrong, right?}

\textit{What's wrong with the kid?}

\textit{A normal child, or rather, not normal, well, I don't know if he's normal or not, but you can't get rid of an innocent child.}

\textit{Master said that it was just a test for the bald bastard (Grand Master Wunue) who was very suspicious and fearful.}

That's why Monk Wunue also apologized.

From the beginning Ximen Surin suggested to Wunue, who was agonizing over the treatment of the child, that he listen to her disciple's opinion.

She believed that her disciple would definitely oppose and show her courage.

She didn't just believe it, but rather thought it was natural, so she admonished Master Wunue without hesitation, telling him to look at her disciple and see what the real Heavenly Slaughtering was like.

But that's all.

Qing also didn't think the task of raising a child was that difficult.

Because the child seemed kind and innocent.

\textit{I thought it would be okay if she grow up with the good disciples of our Divine Maiden Sect.}

\textit{I wondered if she would be as bright and cheerful as the other disciples, and if she could become a gossipy and cheerful person who could laugh brightly.}

\textit{But is that right?}

Of course, Qingdo felt little wronged.

Are you saying that she really have to risk the rest of she life to save an innocent child?

If she's not going to take the child in, wouldn't it be better to just leave her alone?

But what would happen in the future if you leave the child like that?

Even Qing, strictly speaking, was not an official disciple of the Divine Maiden Sect.

She's only a disciple of Ximen Surin, and was an outsider who was not listed on the sect's register.

Only then did Qing understoodd her master's choice.

\textit{Of course, Master must have been worried about taking on a disciple who had the Heavenly Slaughter Star.}

\textit{If she brought me to the Divine Maiden Sect and then I suddenly turn around and cause trouble, she could be kicked out of the Orthodox Wulin. No, it would be fortunate if she only get kicked out.}

\textit{Even so, didn't she took me in as a disciple and even pass down her surname to me?}

Yes, she passed down the surname.

It means that if there was a problem later, she would take responsibility.

In fact, now that it's come to this, if Qing were to say one word about officially becoming a disciple of the Divine Maiden Sect, she would immediately be accepted as the youngest Elder.

But she didn't know that back then.

At that time, he was just a vagrant who came from nowhere, so how could he suddenly take him into the temple just because he saw something he liked?

In reality, he was a homeless wanderer, so he was called a vagrant.

He was also a murderer who killed and robbed people of their evil deeds.

But did I ever have such thoughts?

Since she couldn't stop walking at all, Qing crossed the mountain temple in a way that seemed very leisurely to others.

An artificial Heavenly Slaughter Star.

To be honest, there were several moments when it was dangerous for Qinghan too.

Even in the Demonic Cult, I was trying to get rid of Heimae by blinking my eyes, but was it because it was not helpful and not fun?

Because I needed strength, I jumped into the gate of the horse several times.

Even if that were not the case, in times of crisis, there have been more than one or two instances where the true energy of Buddhism and Taoism, or rather Confucianism, has cleansed the mind.

Of course, the child won't be to that extent.

There's no guarantee that it won't be that bad.

Can I do it?

But how?

It's not like I can learn so many different skills.

Qing thinks of the Giant Pagoda Emperor and the lamas.

Qing was holding the new skills they had learned in his dantian.

Even those cruel and ruthless bastards had the true teachings of Buddhism within them.

It was a Mahayana teaching that teaches us to pity all living beings and to practice virtue so that we can enter nirvana together.

But what were they like?

In fact, I still feel like I haven't come to my senses yet, but at least the ridiculous things he said about the Xijang people must have been sincere.

Whether that sincerity was right or wrong or whether it was a completely rotten, ugly greed was a separate issue.

Even if it was a stubbornness that had hardened into a habit of self-deception and self-masturbation, he would not have hesitated to act on what he believed.

I felt my heart sink.

No matter what kind of divine power was imparted, can it really help the child?

To a child who experienced a harsh childhood, a time when his worldview was formed, and where nothing but murder was happening?

No matter how much it teaches compassion and love, if a person sets his mind to it, it was nothing more than a tool to harm others; it was nothing more than a sword.

That was the essence of martial arts.

The art of harming others.

Martial arts train you to drain your opponent's weapons and exploit their weaknesses.

Beasts cannot carry weapons.

A skill solely for dealing with people.

Martial arts were the art of killing.

Finally, Qing's footsteps stop.

Now, one step to the corner, turn here and you'll see the child.

If anyone saw it, it would appear as if Qing was hiding behind a pillar in an unknown Buddhist temple in Sansa.

but.

In this harsh world, in this primitive, ancient, and uncivilized age of slaughter, how could a child survive without martial arts?

Qing recalls the horrific days of that difficult first year.

How can a stranger who knows nothing about the world survive when thrown into a completely unfamiliar world?

At least my body was strong, so I managed to survive by eating everything that was inedible. Otherwise, I would have died a long time ago.

And the child was no different from himself.

No, but would I have been better?

My world taught us that at least human life was precious, so I taught you to believe that.

Even if morality was nothing more than a kind of social rule created for the greater benefit of society, as it was established that the social loss of killing one another was much greater than that of saving one's life, it was still a good thing because they lived well and fell.

A child's world may have been much shorter than mine, but it must have been a cruel hell that I wanted to deny.

Besides, what if the child was like me?

If the whole process of tearing, cutting, and tearing people apart and making them cry out in pain and despair was an unbearable ecstatic pleasure.

Can you ask a child to endure this for the rest of his life?

Right now, I'm having fun catching bad guys?

A child cannot live without martial arts.

Qing can't stay by your side and protect you for the rest of your life.

That won't do either.

No one in the world can, and should not, be cared for by someone for their entire life.

Those were pets, not people.

I will have to teach martial arts.

why?

For the child to protect himself.

And if you have a thirst for killing, there was a proper way to quench it.

No, no. There was no such thing as a right way to kill.

No, we need to teach them how to kill people without being hated.

"ah."

Qing starts making noises without realizing it.

Martial arts were for protecting yourself.

I understand why there were so many new skills in the old school.

Martial arts were about cutting people down to protect their bodies, but they cannot wash away the wounds in their hearts, so they try to comfort their hearts with kind words.

The Sutra of the Heart of the Lord, the Sutra of the Heart of the Lord, the Sutra of the Great Compassion, etc.

Yes, martial arts was a means of protecting me.

Are the only things to fear in the world only swords and fists?

How painful was hatred and enmity.

Bad guys must die.

Because it's the right thing to do.

The innocent must live.

I hope good people were happy.

At least that's what I hope it will be.

Otherwise my heart will hurt.

And I want innocent people, good people, to love me.

I wish you would at least give me a look of affection, even if it's not to the extent of smiling at me, praising me, or making a fuss.

I've never really cared about justice or cooperation or anything like that.

The reason I move was because I'm a selfish little shit who was born like this.

And that's where the martial arts come in.

Suddenly, somewhere in her heart, a path grew.

It was a path that passes through a rugged and insurmountable mountain range with cliffs gaping open on all sides and mountains rising as high as swords.

But there was a way.

When there was no road, it was just part of the scenery that was visible to the eyes.

But once it was connected to the unfolding path, it was no longer a landscape, but an obstacle that she must walk through, pass through, and climb up to overcome.

The direction to go, the direction that martial arts should aim for.

Now, the moment when the martial artisy who has climbed the mountain and reached the thought of where to go finally has a destination, is the moment when she reached the Middle-Stage Unrestrained Realm.

Qing's lips draw a soft curve.

It was a very annoying smile.

\textit{This body. The Middle-Stage Unrestrained Realm, achieved.}

\textit{What is possible in the Middle-Stage Unrestrained Realm?}

\textit{I need to show those pathetic kids of our Half-Sword Double-Saber Association what a real master is.}

\textit{If this continued, won't I end up reaching Late-Stage Unrestrained Realm this summer?}

Qing took a step forward.

Just like she always did, she walked straight ahead without hesitation.

It was a gait that cannot be corrected despite Ximen Surin's countless bombing run, but rather, had maintained its state and evolved gracefully.

With strides as long as her slender legs, she walks gracefully and gracefully.
