\chapter{Bound Together (6)}

Originally, it was planned to be a commemoration of the mid-term of Hwagyeong and to greatly boost the morale of the dear members of the Half Sword Ssangdohoe.

However, there were no special skills that become more possible just because it was a mid-level painting.

Come to think of it, for these lowlifes, neither the early nor mid-stages of Hwagyeong were worthy of being looked up to, so I wonder if it would be of any help.

The difference between five thousand gold crowns and ten thousand gold crowns may seem large, but if you compare ten billion gold crowns and eleven billion gold crowns, the difference was actually greater. But anyway, it's a lot of money, so wouldn't you do it?

Of course, not for those with billions of won in assets.

It was heartbreaking for Qing, who was already a master of the art of painting, that he cannot make this great achievement widely known.

So what? I, the adult, have to endure it.

Isn't it my heavy responsibility to have as friends these unmanned appellants who cannot even recognize the footprints of this giant?

So I decided to brag to the elders.

"Are you talking about the mid-term?" "What?"

"……Considering the disciple's qualities, this isn't all that surprising. Excellent, the disciple has chosen the path of the sword."

It was a reaction that was about three beats late, even though it was not surprising.

Qing maintains a fresh expression on his face.

There doesn't seem to be much of a smile here.

But to the three Hyeon-gyeong masters, it was beyond shocking.

Didn't you climb the mountain last fall?

Mid-winter?

So, do you go to Hyeon-gyeong in late spring or summer?

Well, that's not true, though.

Even if you say it's the mid-term of painting, it's still the stage where you decide what you really want to study.

If you already know your sword and clearly know which sword you want, you may be able to climb quickly.

But there were quite a few people who wandered throughout their lives in the early days of Hwagyeong.

Because it was difficult to clearly understand the human mind.

Moreover, it was a time when you must deny the martial arts that you have taken for granted as a firm truth and cover it up with your own imagination.

It's easy to say, but before the Thousand Flower Sword, it takes at least thirty years of training, and how can one so carelessly deny the fundamentals of martial arts that this beginner's technique and this mental image were the most clear answers?

Oh. Is that why?

Wunue tries to somehow convince her.

The youngest martial artist, I don't know when he first started holding a sword, but it must have been at most ten years.

Rather, isn't it because I've spent less time blindly believing in my own martial arts that I've been able to find my own path and direction more easily?

Ximen Surin also had roughly the same thought.

I am a disciple who can learn many things, and how many things have I learned from my maternal grandparents?

So, rather, as he experienced various martial arts, he would have less of the worship that martial artists usually have for their martial arts, or to put it nicely, pride, or to put it badly, the stubbornness that his own was the right answer.

Nan-Gong Daero just stopped thinking about it.

Hmm. That's awesome. Hmm. That's awesome.

Anyway, Ximen Surin was just satisfied.

The remaining two Hyeon-gyeong masters were a bit more complicated.

However, there was no reason for the two of you to adjust your level of thinking, so just leave it as it was and let it be.

Qing straightens her posture and raises her back.

"Master, I have carefully considered this matter and have decided that I wish to take the child in."

"Well. Your disciple isn't that old yet, but considering his accomplishments, he's certainly qualified to be someone's teacher. However, taking on a disciple also carries a certain amount of responsibility, so it's something you shouldn't take lightly. Remember this."

Ximen Surin gives some words of advice.

Qing opens his mouth again.

"I thought that the adults that children need and desperately need right now were not teachers who will teach them, but parents who will care for them."

A wrinkle appears on Ximen Surin's forehead.

Actually, it's not that appealing.

Even though the year has passed, she was only twenty-two. Well, if she was a married woman, it wouldn't be strange if she already has a child.

The marriage of female warriors came much later than that, so in Ximen Surin's view, if a young girl wanted to have a child, it would be difficult to just say, "Your intentions were truly admirable," and pass it over.

However, if a good disciple makes a decision after careful consideration, it was not something that a master can just say no to.

If you had told me when we were alone, I would have objected, saying, "Do you think that's easy?" But, of all times, you brought it up now, so I think you're being really cunning.

So I can only frown and make a displeased expression.

How could the two Hyeon-gyeong masters not know that feeling?

Ambassador Wunue steps forward to take care of Ximen Surin.

"Hmm, your thoughts truly reflect the Buddha's will. However, keep in mind that this will not be an easy decision. Furthermore, you were not a perfect child."

"That's why I thought that he was a child who needed his parents more than his teacher."

"Ahem, raising a child was no easy task. Isn't it, you know?"

"Senior, you're right. Raising a child—no, a child—isn't it something you can just do as you please? He never listens to anything, no, not even a single thing. I thought I raised him well, without any shortcomings, but this kid… Whoa, where on earth did it all go wrong?"

Nan-Gong Daero's persuasion was somehow imbued with a very heavy sincerity.

But Qingdo Qing had his own thoughts.

"Actually, I don't want to solidify a strict and serious relationship. Right now, the child needs their parents more than their teacher. If I had to say something, it might sound a bit harsh, like family play—Hmm, play—but when the child grows up and has a more mature mind, won't they understand?"

The reason Qing took on the role of father and the plan to produce countless mothers through infinite mother proliferation were all for that reason.

To begin with, Qing didn't have much confidence either.

How do I raise a child?

I thought other people's kids would be cute, but I never thought about it, so of course I was completely unprepared for this situation.

Isn't the reason a human child spends ten months curled up in the womb to prepare for parenthood, to prepare their hearts for that?

"Hmm."

At first glance, it sounds okay.

Because in parenting, there was absolutely nothing that was always good.

I wish my child would grow up and understand what I meant to him, but hey, some people still resent their parents even when they're old enough.

Ximen Surin sighs deeply.

"Since your disciple's intention was such, and you have thought carefully about it, I believe you were already qualified to take in the child. If that was so, I will no longer dissuade you."

like this.

Official adoption declaration, complete.

The cleaning of the Blood Thunder Temple, which had been decorated with internal organs and flesh, was roughly finished, so it was time to end the expedition and return to Kunlun Sect.

And Qing faced a very big problem.

No, Ciyu was illiterate!

What a blind person who doesn't even know how to read!!

Of course, there was no way that the blood cultists would teach their children to read and write.

There's not even enough time to instill hatred, what kind of words were there?

And in fact, half of the people in Zhongyuan were practically illiterate, unable to read even half of the Thousand Character Classic.

Even if I try, I can only write numbers in my name, and even then, I don't know how to write the rich.

For reference, this was what a person with talent was like.

The one with the most virtues was one and the other.

Numbers were likely to be altered and used for crime, and since basic numbers were easy to change by drawing more lines, they were letters that were made to be difficult.

So if the world listens, what's the problem with illiteracy? We can all communicate anyway.

A child of that age would inevitably not know how to read and write, so you might say it's strange that he reads and writes well.

But it was a very serious matter for Qing.

Well, that's because he's from Qing dynasty.

Oh my goodness, illiteracy.

How can that be?

In order for a person to live like a human being and not be sad, he or she must learn to read and write.

Because it was common sense to Qing.

Thus began Qing Dynasty's Thousand Character Classic class.

"Now, look. This is Tian (天). It means heaven."

Ciyu gazes blankly down at the thousand characters carved into the ground.

Qing prepared to answer him.

A line was drawn over the shape of a person, so it means the sky.

However, Ciyu turned her head away from the letters and looked at Qing's sword, making Qing's own education preparations at eye level embarrassing.

"Knife."

"Why? Should I teach you how to use a sword?"

Ciyu nodded vigorously at him.

"Hmm. It's still too early for you, but there's nothing I can do. Now, look."

Then, as Qing swung his sword, the starlight created by man left deep scars on the frozen ground of the winter Qinghae.

Sword, sword.

"Okay. This was the sword. This was the sword sword. The sword was much easier to use than the sword, isn't it? In fact, that's why the sword was called the king of all weapons. Hmm. But."

Qing swings his sword again.

Twin swords.

"If the sword was difficult, can I write it like this? Okay, then let's start with the easier letters. Sky, Heaven. Okay, remember?"

Dori dori.

"Hmm. Don't you remember? Then you can look at it and write it down. Okay, let's try writing it down."

And then.

Qing felt dizzy.

Moon Il-ji said that teaching one person will awaken ten others.

But Ciyu was on the tenth day of the month, and even more so, Amitabha Buddha.

If you teach ten, you will awaken one, and if you teach ten again and awaken another, you will forget the one you knew before.

Qing's eyes went dark!

\textit{No!}

\textit{Ciyu is a stone head!}

\textit{My daughter is dumb!}

She was a woman who hesitated while writing the character for "지" and was secretly looking around.

Qing-i pats Ciyu's head and pats it.

"Hmm. Ciyu, you're a very generous person. They say great people were slow to grow, and a large vessel takes time to fill. Ciyu will become a very great person. Hmm. I'm so proud of you, I could almost cry…"

Qing felt a great wall from the beginning of the Thousand Character Classic.

I feel like I'm constantly checking others' reactions, doing it because I'm told to.

Wouldn't it be obvious that he was bored and not having fun?

This was not the kind of writing study that Qing had in mind.

This was the sky, this was the ground, huh? Me? A person? Yes, that's how people write. I thought, "Isn't it okay to teach one or two letters with this kind of emotional feeling?"

But what the hell.

Well, studying was not fun.

So, how can we get children to learn more actively?

Of course, of course I don't know how to do that.

If I had known, I would have already become a prodigy and become famous in my hometown, become a great figure, and enjoy the glory of the nation.

If not, wouldn't it be like this now, playing video games?

Hmm. Now that I think about it, it doesn't seem so bad, except for the fact that the peppers fell off.

It's a real shame that I can't let Ciyu play video games.

You never know, right?

Ciyu might also be able to travel to the future world and fight against the invaders from another dimension, becoming a millionaire and enjoying immense wealth and power.

It's so vague, I just have empty thoughts.

It's definitely not easy to raise a child like this.

Qing tried to take a deep breath, but no, she had a child and couldn't sigh openly.

Of course, Qing had a trick in the form of the Ximen Surinryu teaching method, which was the best educational expert in Zhongyuan and the highest authority on etiquette and manners instilled in him.

But, there was no time for this little thing to hit, and in fact, Qing had no intention of adding more punishment to a child who had been beaten up so much up until now.

\textit{When she's about fifteen or sixteen years old, I should probably start to discipline her with some love.}

\textit{Hey, you two were all behind.}

\textit{Let's see when Ciyu get older.}

\textit{At that time, she will realize that the greatest of faith, hope, and love is a nuclear attack.}

\textit{Well, I guess it doesn't matter yet.}

\textit{She's still just a baby, how can she learn letters?}

\textit{As long as she have a healthy body, that's enough.}

\textit{Eight years old would be, um, first grade in elementary school, right? First grade seems a bit early to be writing Chinese characters.}

\textit{And what, our Ciyu doesn't seem to be a liberal arts major, and she doesn't seem to be a science major either, but still, in this primitive ancient Zhongyuan, the best profession is the arts, or rather, excluding arts, the best profession is the sports major.}

\textit{And even if she's just a fake Heavenly Slaughter, she'd definitely have incredible talent in martial arts. It's a lottery ticket that you know will win without even scratching it.}

\textit{Hmm, what should I do?}

\textit{If the child becomes a genius of the century like me and grows up with martial arts skills.}

\textit{I was worried that since she was already a child who had seen enough blood, she might be learning too quickly and have adverse effects.}

It wasn't something she should have worried about from the beginning.
