\chapter{Bound Together (1)}

\textit{Where am I, who am I?}

When Qing-i suddenly came to her senses, she found herself sitting in the guest room.

Qing blinked his big eyes again and again.

Oh, when was I at the restaurant?

But the doubt was short-lived.

So what, were you okay? Do you feel okay?

Looking at it, this inn was no ordinary inn.

Something delicious smells, the scent of fresh blood, and it's starting to waft.

I guess I'll have to eat something and think about it slowly.

"Here you go, Jeomsoi!"

"Yes, sir. Would you like to order?"

It was an amazing service, with someone appearing from behind as if they had been waiting for a long time as soon as I called.

But the outfit was a bit.

"Huh?"

Qing examines Jeomsoi's outfit.

He wore a silver vest over a white cloth, and a black coat over it.

The nape of the neck, buttoned all the way up, had a butterfly-shaped fabric decoration hanging from it. Wasn't it a Western-style garment called a yeonmibok?

What? Is this the introduction of Western civilization?

Of course, this was unlikely, as black suits were not popular in the Western Regions at the time.

Rather, it was a time when people were getting sick of wearing such a dull black color.

But Qing doesn't know. How could he know?

"Uh, um. What were they good at here?"

"Here was the menu."

Huh. A menu?

Qing accepts the board with a bewildered feeling.

In Zhongyuan, a table setting was a kind of extremely cheap thing that was only hung in small restaurants where you can get a meal for a few pennies.

It was only in small restaurants that they do not have anyone to serve customers other than the host that they write it down and hang it on the wall.

Because the dots were human figures.

It was the cutting edge and humanistic essence of Jungwon, recommending the best dishes based on the day's ingredients, seasoning, and the customer's food preferences!

So, Jeomsoi was also a high-level human resource.

It was not a job that just anyone can do, as it requires a good impression, sociability, tact, humor, and even connections.

Then suddenly, he chuckled.

I've become quite Zhongyuan person.

It's been a few years since the table setting became awkward.

Separately, Qing understood the situation.

What the heck, this was where it is.

The land I've visited dozens of times.

Isn't this the gateway to the horse?

Qing leans back comfortably in her chair.

Then, step by step.

Of course, there was a customer who was sticking his butt out across from the table as if it were his place.

A celestial body swirling where the head should be, a pitch-black void and destructive starlight flowing across the top, bottom and center.

"What was it? Are you tired of this sloppy scenery? But what was this? Are you spying on my memories? Or not? Since it's a star, does it rise in the West? Did you make it after seeing the people of the West?"

Then the scenery of the guest house changes.

In the present Zhongyuan, a landscape only Qing can recognize, the vast universe unfolding around the dining table, and countless blue stars passing by, compressing eternity into a fleeting moment.

Qing understood what he meant.

This friend also said that the world illuminated by stars was not only in Jungwon.

Now that I think about it, I think I heard that the evil star spreads its starlight throughout the three thousand worlds.

But I didn't know that the Three Thousand Worlds were these Three Thousand Worlds.

No, but if you put it into words, what was it, this visual, well, it's a spectacular sight.

The evil spirit silently places his hand on the table.

He lifts one of the drooping eyeballs and flicks it with his finger.

Eyes rolling in front of the blue sky.

"What was it? A gift?"

[Do you want?]

It was only then that the evil voice blurted out a word.

"Ugh."

Qing looks at the eyes with a disgusted expression.

Because the eyes were tangled and wiggly with long, optic nerves.

Separately, something that suddenly comes to mind.

Was it in Mount Lao?

A vision I saw while killing the bastards of Sapa.

The memory that reflected the evil deeds of the past.

"Is that what you showed me? But, no matter how much I like it, this was a bit… tempting."

If you could see someone's evil deeds, wouldn't you be able to tell at a glance whether they were worthy of death or not?

But still, this was a bit much. What, you want me to put it in without looking at it?

Then the eyeball changes shape.

It was a sight quite familiar to Qing, a precious object called Aeche in Zhongyuan, a pair of glasses.

"Oh, that's a little better. No, if you can do it, why? You always try to fill the void by bragging about your long-term skills."

Qing giggled and reached out his hand-

Suddenly stopped.

"No. That's suspicious? What's going on? A gift all of a sudden? It's not like we're exchanging gifts on friendly terms, right?"

Then, the evil spirit reveals a sinister smile. That's how I felt.

Even though there was no way that an expression can be shown on a celestial body that was empty anyway.

And then it just disappears without a trace.

As if telling me to do whatever I want, whether I take it or not.

I feel like there's definitely some kind of plot behind this.

Qing stares at the body on the table.

And slowly reach out your hand-

match!

In that moment, something dark and rough hit Qing's wrist sharply.

A sharp pain that feels like your wrist was breaking.

"omg!"

Qing suddenly sits up.

I thought to myself, rubbing my aching wrists hard.

The thing that hit my wrist, I'm sure I've seen it somewhere, yes, it was a tree branch, it was definitely a tree branch.

Then suddenly, I feel someone's gaze on my cheek and turn my head.

All I can see were pitch-black eyes that fill my field of vision.

"Huh."

Aren't those unusually dark eyes staring at you quietly without moving at all?

Somehow, the luster felt dull, and the lifeless eyes just looked quiet and silent.

"Um, were you awake?"

"Come here, sleep more……."

Then, from the other side, a voice still clinging to the dream answers.

Hmm. Except for you, Gunyeong.

But now even sleepwalkers call themselves by their names in the third person?

what?

Is our mental age getting lower?

Anyway, I don't have a hobby of waking up sleeping people, so I'll leave it alone.

Qing looks at the child looking at her.

"Um. Hello?"

When Qing waved his hand, the little boy briefly looked at her long, white fingers, then returned to looking at the most beautiful face in the world without answering.

It doesn't seem like you understand at all.

Do you not know Korean?

"[hi?]"

But there was no response.

Qing tries to use the foreign language she knows.

Since I had never spoken to the Westerners, Japanese, or Easterners in this primitive martial arts world, these were greetings that remained in my purely Qing memories.

But there was still no response.

Well, usually, even if you don't understand something, if it seems like you're saying something, don't you react?

Saying you don't understand or whatever.

He just stared at me silently, so, um, maybe he was deaf? No, but he must have seen my mouth moving, right?

Besides that, he was a child with an unusually low presence.

Standing still like a statue, without moving an inch, if Qing's superhuman hearing hadn't detected the faint sound of breathing, you'd wonder if he was even human.

but.

Are you eight now? Nine? Ten?

It was not the kind of reaction one would expect from a very young child.

Aren't children originally creatures who can't stay still for even a moment?

An expressionless face that looks up with cold eyes without even moving an inch.

The gaze was also persistent on such a topic.

Even while Qing was putting on her clothes one by one, she just turned her head and stared blankly.

Hmm. I wonder if you want something.

I don't know since you don't say anything.

I'm not an expert in taking care of children or anything.

Besides, well, he's not a normal kid.

Qing scratches his head.

No ordinary child was found buried up to his chin in a mound of torn flesh.

The vision I had when I dug up the child and took it out, of a drugged person being mutilated and eaten alive, Hmm.

There were those red numbers above your head.

Urrrrrr, gurrrr!

Suddenly, a tremendous sound, like a mountain collapsing, resonates in the bedroom of an unknown owner.

It's the sound coming from inside Qing's stomach, the sound of her stomach urging him to fill it up because it's empty.

"Aren't you hungry?"

"This was a soup-"

"Grow up, Gunyeong. How can you act cute while sleeping? Hmm. Let me say hello first. Little one, just wait quietly."

Of course, there was no sign of understanding.

Then suddenly, I wondered if it would be okay to leave him with Gunyeong.

Wasn't that the child who had been sleeping since yesterday afternoon while I was cleaning up, washing, dressing, and putting him to bed?

It must have been a long time since I was hungry.

However, the scene where the child was eating was a bit uncivilized.

While Qing was pondering for a moment about what to do, the child carefully got down from the bed.

Although the sight of him crawling backwards carefully because his arms and legs were short was truly adorable.

And then he came up to Qing and stared at her intently.

It seems like you want something.

What was it, what do you want?

Anyway, since there were some parts that were a bit uncomfortable, I feel a bit awkward leaving it like this.

Although it was pretty, it has a faint luster like a glass bead and has an eerie quality.

I thought it might be better to take it with you for now.

It was the moment when Qing bent down and stretched out both arms to hold the child.

As if he had been waiting, he wrapped his arms around Qing's neck and hugged her tightly.

And then, by resting your chin on your shoulder and letting your weight fall, it looks very natural, as if you have found your place.

He ends up laughing bitterly.

Well, he's a kid, after all.

It looks like you wanted to hug me.

Qing leaves the bedroom holding the child, reflecting on herself for a moment, wondering if there was something a little creepy about the child.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Master, this disciple pay my greetings. Did you sleep well last night?"

"Huh. You wake up early."

Ximen Surin's morning was early.

It's very fast.

Old people don't usually sleep well at dawn.

Ximen Surin was already up and sitting quietly in meditation.

But it's not something that happens every day or two that a disciple comes to greet me slowly in the morning.

Above all, Wunue and Nan-Gong Daero, who were stretching in the yard across from him, could not hide their envious eyes when they saw the disciple who came to greet them in the morning.

So, even though his tone of voice was cold, Ximen Surin's expression was somehow proud.

"Have you eaten? Would you like some breakfast?"

"He's not even an old man in the back room, so how could he possibly carry breakfast in his disciple's hands? Yeah, that kid, um."

Ximen Surin was about to say something, but then sighed deeply and waved her hand.

"The child slept all day yesterday, so he must be hungry. Since all the elders were gathered here anyway, how can the master eat alone? So don't worry about me and go back. First, feed the child some food."

After such a simple greeting, we headed to the restaurant.

Since there was quite a lot of food left at the Blood Thunder Temple, the smell was very good from the morning.

Dried fish porridge, a few pieces of boiled dried meat, and stir-fried dried vegetables.

And the never-ending meal of barley flour and honey in Qinghae.

It's a bit disappointing that I'm dressed exactly the same as last night, but I'm not at a guesthouse, so I shouldn't complain about that.

Rather, we should be thankful that the Blood Thunder Demon Sect subjugation force, comprised of the elite members of the Kunlun faction, was able to prepare such a meal.

"thank you for this food."

"Haha, you're so energetic since morning. I think I know the secret to Lady Ximen's achievement of such a noble state."

"Of course. If you eat well, your skills will improve significantly."

The person standing in the kitchen was none other than the tearful Okru Sword.

Cooking was a hobby or something.

After having dinner last night, I felt like I had the skills to be recognized as a master chef wherever I went.

"It looks like the child was awake too. Hmm. Hello?"

Okru Sword waves his hand with a clumsy smile.

But the child just stares blankly and doesn't react in any particular way.

Okru Sword lowers his hand with an awkward expression.

Qing tries to defend the child.

"I guess the child was suffering, but he didn't respond at all."

"Huh. The little one."

Then, in an instant, the corners of Jade Sword's eyes turned red.

Well, it must be so bad that his nickname was Crybaby.

Qingdo was now used to it, so he deftly heads to his seat, showing off his ability to hold several plates with one hand, leaving behind a stream of tears streaming down his face.

And um.

It's a mess.

It seems like the child has no concept of table manners, so he just grabs the food with both hands and eats it.

Even when he tried to eat the porridge with his hands, if Qing hadn't been startled and stopped the child, a disaster could have occurred.

What was porridge?

It was hotter than it appears, and it contains an extremely vicious heat, like a terrifying boiling molten iron that never cools down, like the fires of hell.

When Qing stopped him, the child gave up on eating and ate without showing any sign of regret.

Even though both cheeks were full, he keeps pushing them in, looking anxious as if someone was going to take them away.

This was just a beggar-like situation.

Where should I start, what should I teach, and how should I teach it?

Qing sighs deeply and starts eating breakfast.

Qing always did this when he wasn't paying attention to others, filling his cheeks to the brim, chewing it thoroughly, and then swallowing it all in one gulp.

So, if other people look at it, they'll say that big and small bitches do the same thing.