\chapter{Bound Together (2)}

The child was quiet.

No, rather than being quiet, what should I say?

I think it's closer to no reaction.

If you hug him, he will hug you tightly, but if you put him down, he will just look up at you blankly.

When Qing opened the distance, he just turned his head and looked at me, and when I motioned for him to come over, he slowly approached me and stared blankly up at me again.

So why don't I just carry it in my arms and walk around?

I don't know their exact age, but aren't little kids this age always running around and having trouble sitting still?

And then there's the babbling, come to think of it, Hyang-i was probably the same age as me, and when I think about it, she almost looks like a doll.

"Hey, so cute. What's your name?"

"……."

"Do you want to come to this older sister?"

"……."

But it was ignored!

Jian Buxi's shoulders slump as she tries to talk to the child.

"Hmm, do you think I'm being hated?"

"Can't she hear you? No, she don't even seem to respond. Maybe her hearing was impaired."

Peng Daesan said with a pitiful expression.

Even if you were shy, wouldn't you usually react with some shyness when someone calls you or teases you?

But the child just stares blankly somewhere in front of him as if he didn't hear anything.

Oh, so that's what it was.

Because if you can't hear, you'll also be accompanied by symptoms of not being able to speak.

Qing strokes the child's head with a feeling of pity.

The moment Qing's hand touched his head, the child flinched, but he remained motionless like a doll.

So there were three pitiful looks.

That was when.

"Young Lady Ximen? Oh, you're here. The Great Monk is looking for you."

"Oh, yes. I'll come see him now."

As Qing stood up holding the child, the Kunlun sect warrior who had been speaking cautiously spoke.

"He asked for you to leave the child with your friends."

"Ah. Yes. Hmm. Yi-mei?"

"Yeah. Yeah."

Jian Buxi smiles brightly and extended her hands.

I thought that if she was the absolute ruler of the pedestal, the clear empress of the pedestal, the best pedestal queen in the world, then even the child would have no complaints.

As she handed the child over to Jian Buxi and left the nameless Buddhist temple, Qing felt a gaze on the back of his head.

Well, it's actually a bit difficult.

Even a child needs to have some childlike cuteness in order to be able to be loved as much as possible.

Besides, the visions I saw while rescuing him were clearly of a mentally ill child, so I was cautious about petting him carelessly.

Besides, Qing's cuteness was originally very extreme.

Because he tends to be the type of annoying uncle who makes his nephew cry no matter what.

But since I couldn't do that to a sick child, I just held him in my arms and stroked his head.

Well, if only the kid had been a little more clingy.

Well, it would be strange to live with that kind of appearance and still be attached to it.

When I entered the room, the three elders were gathered together and waiting for me.

However, somehow the atmosphere itself does not feel very harmonious.

It was obvious that a heavy topic was about to come up, so Qing gave a brief greeting and sat down quietly on the cushion.

The Zhongyuan was a standing culture, but Hyeolryeumsa Temple was a temple, so it seems that they lived a sitting lifestyle.

"Is the child well?"

"Yes, she's a bit too quiet for a child. I wonder if she might have hearing problems."

"That may not be the case, Amitabha……."

Ambassador Wunue prayed to Buddha with a sense of pity.

Then, the three elders exchanged glances with difficult expressions, and then Ximen Surin sighed deeply and spoke.

"Manra Daehyeolmyeol Cheonjin said that the child who borrowed the power of the evil spirit inherited the karma of a thousand years through his terrible deeds. How pitiful and pitiful."

Lock the child in the room.

It's not dirty because the child shouldn't be harmed, but they keep all kinds of animal feces and rotting corpses in a separate space blocked off with iron bars, which creates a bad smell.

The room he was locked in had no lights, just a small eye hole.

All the child could do was stare blankly out through the hole.

And the child sees the world through a hole.

It was a world where everything a child could not have was spread out.

The beloved children walk holding their parents' hands and look like the happiest people in the world.

Children play and laugh with their friends, and sometimes they hold a grand banquet with delicacies from all over the world.

The child was forced to watch the sight of his father enjoying all the things he could not have.

Sometimes the child would come out.

But what comes back was complete disregard.

It's just an appearance as if the very existence itself has disappeared.

Since the production of the murder took place in the village of the Blood Cult, everyone was an accomplice.

In this way, the child's world becomes filled with hatred.

He was a child who has been instilled with hatred to hate the world so much.

"It's said that in ancient times, all children born in the year when the evil star of the Heavenly Slaughter revealed its tail and took its place in the celestial sphere were killed. This was because the bearer of the Heavenly Slaughter was such a fearsome being."

The ominous sound made in front of the thousand-year-old master make Qing's heart sink.

"In the records of the past, when the Blood Cult was wreaking havoc, how many times was there a Manra Daehyeolmyeolcheonjin? And how many times was the poor child used as the core of that chaos rescued?"

In half of cases, the child was found alive.

A child whose hatred and life force has not yet reached that of a thousand years old cannot withstand the cruelty of the truth and ends up dying.

So, if a child was rescued, it means that he or she can withstand the evil spirit of the evil spirit, even if it was imperfect, after his or her heart has already been dyed black.

"Throughout the long history of martial arts, there have been many elders who, out of pity for a child, wished to take them in. And each time, without fail, a great murderer would appear in Jianghu and shook the world. Children who learned martial arts grew up to become renowned murderers. Even without martial arts training, they would rip open the dantian, cut the meridians, and poison the weak children, even wiping out entire villages."

"Oh, then, what about the child…?"

"Hmm." "Um." "Namu Amitabha Buddha……"

The world's most powerful masters, unrivaled in the world, all avert their gaze.

The blue eyebrows form the shape of the number eight.

"But that's too much. What did the child do wrong? Even if it's as you said, how can you punished a child who hasn't do anything yet?"

Then, Wunue asks in a sad tone.

"Then what should we do? A child who will surely become a great danger to the world—"

"That's something we don't know yet."

Qing-i interrupted Wunue's speech.

It was truly rude, but would it be a comfortable thing for a scholar like him to say such things?

But even so.

Even though the evil deeds were already engraved in red letters and the child has accumulated enough karma to eat human flesh.

It wasn't her fault.

Qing corrected her posture.

"Confucius said, 'Hear much, but if you have doubts, listen not.' 'Hear much, but if you have doubts, pretend you haven't seen anything.' How can people judge without their own ears and eyes, and rashly decide such a grand matter?"

"But doesn't the conclusion reached through extensive experience speak to the same argument? If it were just one person's words, like you I'd dismiss them, but the same thing has happened countless times in the world. Do you intend to repeat the same precedent?"

"Wang Chong said that the words of the sages often contradict each other, and if you don't understand something, you should ask Confucius."

Qing swallows hard.

"He also said that when a spider builds a web, some bugs get caught and others fly past without being caught. When a hunter sets a trap, some animals get caught and others don't. When a fisherman casts a net, some fish get caught and others escape. Since there's no certainty in the world, we can't assume that a child's future is already determined by his or her nature to kill."

"Aren't you just trying to save the child out of a sense of immediate need? What if a great tragedy occurs as a result? Is that the right thing to do?"

"Zhuangzi said, 'The mind is like a net.' Harming a child seems at first glance like preventing future misfortune, and it's both rewarding and convenient. However, harming an innocent child for something that never happened is absolutely not right."

Isn't that what's right, but what's convenient?

There was also criticism that since there was no precedent for overcoming the murderous nature that had been created so far, they were trying to give up from the beginning.

Then, Monk Wunue wiggled his eyebrows.

"Ha. You're quite the writer. Okay. Then what do you intend to do? If I save the child, do you intend to personally teach her virtue and righteousness and make her a human being? Or are you simply going to hand her over to the Divine Maiden Sect and let her grow up by her own?"

When you got told to choose the difficult and uncertain way, because you refuse the easy and convenient way, what on earth are you going to do?

"That……"

"It's impossible. If the child grows up and fails to overcome her murderous tendencies, the world will point fingers at the Divine Maiden Sect for unleashing her murderous nature. And, more than anything, if that murderous nature seeps into her very bones, the safety of our disciples will be in immediate danger. I've resolved not to refuse the women who come to us, but I cannot help but cherish the children I already hold in my arms even more."

These were the words of Ximen Surin.

Qing bit her lip.

\textit{To be honest, I did have that thought.}

\textit{Wouldn't it be okay if it is a Divine Maiden Sect?}

\textit{I thought it would be a good space to hold and embrace a child.}

\textit{But, what Master said is correct.}

Even to Qing, the Divine Maiden Sect family was much more precious than a child she had never met before.

And that would be the same for everyone.

Even if the child was saved, who will take care of it?

The Wulin Alliance? Shaolin? Shaolin was a place for monks, so it's impossible.

But even so,

"…I will take her."

"Are you sure?"

"I'll take her in and raise her. If she can't overcome her murderous tendencies, I'll take responsibi-"

"Enough. That's enough."

Qing's words, which had been spoken with great solemnity, suddenly stopped.

It was because of the two people, Wunue and Ximen Surin, who had smiles filled with a strange kind of pride.

"I understand Disciple intentions, so no more words are needed. How can it be right for a disciple who is still so young to take in a child?"

"Oing?"

"Even though you have been carrying the karma of Heavenly Slaughter, I have seen your righteous nature, so how much more so can a person overcome the evil nature that has planted against her own will?"

"Huh?" "Huh?"

There was two sounds.

One was Nan-Gong-daero.

"Senior? What do you mean?"

Wunue looked at Ximen Surin.

When Ximen Surin nodded, Wunue smiled brightly and continued to speak.

"This child, the Heavenly Blossom Sword is the master of the Heavenly Slaughter Star of the present time. Your realm is still too low, so you may not have noticed."

"Hey, senior. You're saying it's not enough?"

"Hmph. Judging by the way you can't recognize the Heavenly Slaughter Star even when she's right in front of you, it's clear that you're still lacking."

"I thought she was a bit too much, but well, um, um. Well, I guess that could be the case."

Nan-Gong Daero naturally omitted the part where he said that he was the disciple of his senior godmother.

Knowing the right answer was a natural way to survive, a skill that comes from having already been hit many times.

And then the surprise comes.

\textit{Heavenly Blossom Sword the Heavenly Slaughter Star of the time?}

\textit{This kid?}

\textit{I heard rumors here and there that she was a young dragon with both talent and wisdom.}

\textit{Of course, there were some strange rumors about her being quite vicious, but I thought it was just a slander that usually follows someone who was famous.}

That might also be true.

But, no matter what anyone said, wasn't the attitude of the Heavenly Blossom Sword that had just unfolded before his eyes an example of a dignified and courageous warrior?

It's better to be cruel than too soft.

The martial world was ruthless, so shouldn't the warriors also know how to be ruthless when it's time to be ruthless?

Especially in times like these, when there were constant signs of a blood cult rising.

That's how Nan-Gong-daero understood.

In fact, he was lenient towards her because she was a junior he originally had a good opinion of.

If Heavenly Blossom Sword had been called Heavenly Blossom Dao or Heavenly Blossom Spear instead, he would have thought about it more seriously.

\textit{Is it okay for the current Heavenly Slaghter Star to be a martial artist in the Orthodox Wulin? Even now, she has terrifying achievements, but if she becomes an even greater master and truly becomes the Sword King or the greatest swordsman in the world, and suddenly turns around, would there be anyone who could stop her?}

\textit{But isn't it a sword also a sacrificial tool used since ancient times, a symbol of sacrifice that connects with heaven and also a tool for self-cultivation?}

\textit{It's only natural that a swordsman with that much swordsmanship would be able to overcome her true nature.}

Although the Sword King kept drinking alcohol and complained about his children, in the end, children grow up imitating their parents.
