\chapter{Bound Together (8)}

The child that Qing sees was a child who was observant.

The behavior of quickly rolling my eyes and stuffing food into my mouth when it appeared in front of me disappeared after only a day or so, so now I just sneakily look at people and check whether I can eat it or not.

It was also a characteristic that was not usually seen in children, or rather, should not be seen.

Aren't children, by nature, the embodiment of selfish thinking that only they were important in the world?

It's a child's nature to feel satisfied only after he gets what he wants, but it's really annoying that he can't say anything and just quietly watches.

I'm guessing you probably have similar concerns as me.

One day, I might suddenly be afraid that the things that were given to me might disappear.

I was worried that people would react with malice like the blood cult's dogs at my every word or action.

I don't know Ciyu's exact feelings.

How would I know if you didn't tell me?

Instead, I can give you a few hints on how to buy favors.

Affection was not something you expect others to give you, but something you have to earn through your own efforts. That's what relationships were all about.

So, in Kunlun Mountain, Ziyue, who had washed clean and dressed neatly, appeared before Ximen Surin.

Ciyu, who had come forward slightly, glanced at Qing as if asking for help, but Qing simply nodded.

"Hmm. Why are you so silent? If a girl has something to say, she should say it confidently."

As Ciyu was clearly hesitating and hesitating, Ximen Surin asked the child a question.

The child, with his neck cringing, barely manages to force out the one word Qing tells him to say.

"Grandma, hello……."

By the way, it was the perfect pronunciation that Qing had instructed.

Ximen Surin's eyes widen at the surprise bellybutton greeting.

And then, automatically, the corners of his mouth loosened and drew a faint curve, and his eyes followed suit, opening like a crescent moon.

Ximen Surin coughed in vain, perhaps because it was a reaction she didn't realize she had, and tried to put on a stern expression.

"Why do you call this old woman ‘grandma'?"

"Hey, Master. What difference does a teacher or a parent make to a child? They're still too young to be strictly taught etiquette."

"Ahem, at that age, you should be able to recite elementary school textbooks."

Ciyu's shoulders hunched, and she was busy glancing around, checking the expressions of Qing and Ximen Surin.

Ximen Surin was startled and gestured to her.

"Oh, dear. Come here. I know your situation isn't easy. Yes, that's right."

Only then did Ciyu ran up to her and hugged her, and Ximen Surin's face brighten up.

\textit{Anyway, Master is too concerned about saving face.}

\textit{She's just a brazen brat who had taken over the arms of the Zenith Among Women.}

If it's the knees, it might be okay, but if it's the bosom, it's an area that even the disciples haven't been able to invade, so this was the special privilege of a granddaughter.

'Spoiling a child? I don't know what you're talking about.'

'Education? Mom and Dad will take care of it.'

"Oh my, why is the baby so skinny? Let's feed him first.'

It was the ultimate filial piety, the irresponsible pleasure of simply covering everything up and being pretty.

(On the condition that they will avoid childcare.)

It was then.

"Well, it's a beautiful sight. If you liked it so much, you should have married a long time ago. By now, you'd have a real great-granddaughter, or maybe even a great-great-granddaugh—"

"Shut up."

Master Wunue, who appeared quietly in the guest room of the Kunlun School, makes a noise that was unnecessarily annoying.

There was no way that the Wulin's Greatest Master would needlessly irritate others.

First of all, because the two were old friends, and secondly, you could guess the reason by looking at his eyes, which were somehow filled with regret and envy.

What was the most sorrowful time  of Buddhist disciples who have left secular life?

"Oh, Monk Wunue is here?"

"Yeah. I stopped by for a bit on my way here. Come to think of it, you said you'd do Depilation-and-Marrow-Cleansing, didn't you? I forgot to give this earlier."

Wunue held out his wooden box with a somewhat embarrassed expression.

When Qing opened it, a refreshing yet somehow familiar scent of medicine pleasantly wafted into her nose.

However, it wasn't the explosive scent of the Great Rejuvenation Pill, the great elixir that could completely clear away even severe chronic rhinitis, so it was probably the Lesse Rejuvenation Pill.

Or maybe it was another secret elixir that was unknown to the outside world.

Of course, of course there was no such thing.

The Lesser Rejuvenation Pill of Shaolin was called Lesser because it was made of carefully collected remaining ingredients after preparing the Great Rejuvenation Pill.

Qing roughly guessed why there was a hint of embarrassment in Monk Wunue's expression.

\textit{It seems he also had a Great Rejuvenation Pill.}

\textit{I think he was debating whether to give the Great or the Lesser Rejuvenation Pill, but ended up deciding on the smaller option.}

But what is the Lesser Rejuvenation Pill?

Even the Great Rejuvenation Pill alone was already a priceless treasurey, and wasn't it a precious thing that all the ronin in the martial arts world would wish for if they could just take a tiny bite?

"Hehe, thank you. Ciyu, come smell this. This is the Lesser Rejuvenation Pill, isn't it? It's a peerless elixir that you can't get even with money. The Great Monk said he gave it to you."

"Smells nice."

Even though she was hugged, she kept sniffing and inhaling the medicinal scent, as if she liked it.

Since it was a Shaolin elixir famous for its stability and usability for all constitutions, it seems that there was no one who likes or dislikes its scent.

Qing pretended to be stern.

"What should you say now?"

"Thank you, Grandpa."

Even while being held in Ximen Surin's arms, Ciyu lowered her head as much as possible and exposed her crown.

This was also the result of Qing Dynasty's education in worldly skills.

The closer you are, the more open you are.

If you're not close, be formal.

Grandma only to Master.

As for the installment, should I give it to my grandfather?

Of course, Grandpa would die because he liked it, but if he did, something would happen. Something would happen.

"Haha. The child is already very well-mannered, Sancai, Sancai\footnote{A monk's chanting}."

Ambassador Wunue's expression brightened.

Because a cute little kid, just by being quiet and not fussy, has the fatal power to induce positive emotions in people.

Moreover, Ciyu had already achieved great things, and was already a demon who had received gifts from three of the ten greatest martial artists in the world.

She received a Lesser Rejuvenation Pill from Monk Wunue, Depilation-and-Marrow-Cleansingl from Ximen Surin, and an expensive wooden sword from Nan-Gongdaero. Although the Sword King was somewhat lacking, it was not like he owed her a gift.

The name of her achievement would be something like, 'The day you were born, the entire Wulin whispered your name'.

I feel a bit reluctant to take the throne proactively. But, I guess not.

And even if this little brat was born with the greatest talent in the world, he won't be able to surpass the great Ximen Qing, who was not just great, but three times as great.

While Qing was lost in thought, Ximen Surin feeds the summoning tablet directly to the child.

Then, a great feeling ran down Ximen Surin's spine, a thrill burning brightly. The moment the child's small lips nibbled, there was a joy she had never felt before.

'This is, the child, the child must be fed!'

It was the moment when the grandmother's inevitable instincts awakened.

But the time was the time.

Although it was not as much as the Depilation-and-Marrow-Cleansing, the melting potency moves the gulp of the dragon.

Next, Ximen Surin touches on the child's pressure point.

Pressure point was a term used to describe acupuncture points that put people to sleep. It was very mysterious and amazing!

However, there was a side effect called a hangover-like headache after waking up.

However, the process of Depilation-and-Marrow-Cleansing was quite painful and dangerous if the child struggled, so it was an unavoidable process.

Ximen Surin carefully lifts the sagging child and entered the guest room of the Kunlun School.

While the Wulin's Greates Master in the world stood guard at the door, Qingdo quietly guard the yard and concentrates her mind on hearing.

Of course, there couldn't be something unpleasant happening in the middle of the Kunlun sect.

In Taoism, a Zen diet means abstaining from food and also avoiding spicy spices.

Since Buddhism and Taoism were influenced by each other, there were similarities in temple ceremonies that abstain from the five spices and abstain from meat consumption.

And as opposed to good eating, there was bad eating, a diet that deliberately accumulates poison in the body.

This was not talking about food.

A diet designed to build up toxins in the body, a bad eating habit that mostly consisted of only eating things that were bad for the body or things that people should not eat.

Representative examples include rotten things, things that were eaten alive without killing animals or insects, poisonous things, and things that cause hallucinations.

And if there was one food that represents evil, it was human flesh.

According to common sense, the reason why people don't eat human meat was because there was a hole in their brain.

According to common sense in the martial arts world, cannibalism stimulates evil in people and accumulates evil spirits.

It's not surprising.

Because the common sense of Qing Dynasty's homeland and this primitive ancient Zhongyuan were subtly different.

I don't know if it's the influence of the mysterious energy of the universe, or if it's a branch of sorcery that makes what the majority believe come true.

Anyway, Qing saw a real instrument.

It was in the sight of Ciyu covered in sticky, pitch-black goo, as if she had been dipped in glue-like coal water.

After that, Qing started to feel uneasy.

Haven't she eaten a lot of things se shouldn't have?

Does that kind of thing happen to me too?

Of course, there was no need to worry since Qing's meridian had already been taken care of by Sulbyungi.

"They're terrible. Those Blood Cult guys. Huh."

"Oh, the disciple will wash-"

"It's fine. The teacher's hands and clothes' hems are already muddy anyway. Why should she defile the disciple by leaving behind a dirty one?"

\textit{Even though you say that, isn't it just an excuse to wash Ciyu yourself?}

\textit{I feel like Master more happier with Ciyu than for myself, but if it's good for Master, then it's good for me too.}

"I'll send the child off when she wakes up, so you should start getting ready. You can't stay in a foreign land forever, can you? She needs to know what her home is like."

"Well, maybe we should rebuild the house too. It seems a bit small and dreary for Ciyu to live in."

"It's so cold outside, and you're leaving your child to sleep in that desolate house? In that shelter by the river, where the bitter wind blows?"

"Yeah, it's desolate…"

Qing felt wronged.

\textit{It seems that Master was mostly concerned with that desolation, or rather, Master also knew it was desolate.}

"Just stay at my residence. Since the owner is away, you should take care of the house."

Somehow, those words sounded full of selfishness.

Even if it wasn't for Ciyu, Ximen Surin thought she would bring Qing in someday, but it seemed like she's trying to brought Qing into the Elder Residence Hall using the child as an excuse.

Of course, it was true that a house was a special kind of good that deteriorates rapidly if no one lives in it.

So Qing headed to her guest room.

The purpose of coming to Kunlun has already been sufficiently accomplished.

\textit{I roughly knew Yun Yuanying's identity.}

\textit{I also knew roughly about my constitution.}

\textit{I saw Absolute Sword Wall, and as a bonus, I did this and that in Repentance Hall. Repentance Hall was really fun.}

\textit{Now it is time to go home, to my sweet home.}

\textit{But with a touch of desolation.}

\textit{Of course, I need to stop by Kongtong before that.}

\textit{The mysterious old man, who was either Mucheon Daeje or MuQing Daeje, also told me to visit the Kongtong Sect next, so I was lucky that the timing was perfect this time.}

\textit{If he told me to stop by a place like Dianchang Sect, um, wow, just thinking about it makes me tired.}