\chapter{Bound Together (11)}

In the end, there was only one table among these that has real guests.

Of course, no matter how united the disciples were, they could not overcome their instincts.

The Lord of Heaven, the master of my body and mind and the embodiment of the sun that shines down on humanity, was here. How can my eyes not be drawn to the person I long to see just once, who was right here in real life?

So, when I looked around with my eyes constantly turning, I saw that it was a truly suspicious attitude.

However, even so, Qing did not think it was particularly suspicious.

Well, that's because I have a bare face.

It was an attitude that if he showed his face, everyone in the world would naturally look at him.

But it wasn't exactly a wrong idea.

And finally, the Lord I saw did not disappoint the Protestants' expectations. He was so beautiful that I could not have imagined, and I found myself worshipping him anew, thinking, "He was truly the Most High!"

So, the gaze was focused on Qingdo's face or below it, but now I'm used to it and it doesn't really bother me.

Well, I was the type who would flinch every time I looked in the mirror, so how much more so would other people feel.

In any case, it couldn't have been more fortunate for the Protestants.

As soon as Qing party sat down, suddenly, servants carrying large plates appeared one after another and began to lay out food on the table.

What? I didn't even order it?

Is this by any chance a real house?

"Excuse me, I haven't even ordered yet."

"Oh, the person who made the reservation has already placed their order."

Only then did he recall the guards at the main gate, Jihanru, who had run out like the wind, saying they would arrest Qing Qingcheonru.

"Ah. Right. What about you, Musa?"

Then the messenger paused and spoke with the utmost respect.

"I am sorry to inform you, but the senior warrior of Jihanru was not of the Ji clan-"

"No, that's right! From now on, please call me Han-ru!"

At that moment, Jihanru appeared, interrupting the sudden death.

The fact that the three letters Jihanru were a name and can also be read as Zahir was a trivial thing, but it was a good thing anyway.

Just as weeds become flowers when you call them, if the Supreme Being calls you Mr. Ji, then from then on, wouldn't it be enough to live as Mr. Ji?

From now on, there will be no Zahir, only your loyal servant Ji Musa!

Only then did the fake guests realize the meaning and their eyes filled with envy.

This can't be happening!

The Supreme Being himself gave me a surname!

Qing was disgusting.

Didn't you just say it wasn't Mr. Ji?

But you say you're right?

"Uh… was that right?"

"That's right. Now, I've heard that you're well-versed in the art of leading and also enjoy incense. Since you've come to Gansu, you should definitely try the Golden Hui!"

"Ah, Geumhwiju!"

Qing's eyes sparkle.

Qing was a man who had a vague idea about good Chinese liquor.

Geumhwiju was praised as a western liquor, meaning that it was a liquor that represents the west among the east, west, south, and north of Zhongyuan.

Of course, the pride of Zhongyuan people in their hometown was a fearsome thing, and it was a realm of faith that often leads to the use of swords.

When it comes to the pearl of one's hometown, everyone boasts that it was the best in the world with all kinds of praise and adulation.

"Would you do me the honor of asking if it would be impertinent to offer you a drink?"

"Okay, well, the snacks were ready, let's have a drink."

The liquor flows out of the narrow spout of the bottle with a refreshing sound.

But Ji Musa's hands were shaking so much, what was it? Do you have hydrocephalus or something?

However, it was quite common for people to shake their hands when pouring alcohol or something.

"Now, Mr. Ji, please have a drink too."

"omg."

Thump! That's the sound of Ji Musa's knees falling.

It was an extreme kneeling, as if he was going to shatter either his knees or the floor of the pavilion.

And then, with the head bowed and the back of the head exposed, he lifts the glass he holds with both hands and offers it to the person, a sign of courtesy shown to someone whose status he cannot dare to meet.

"No, you can take it easy."

"No! This was more convenient for me!"

"No, um. Well. Just take it for now…"

In response, all the fake guests scrambled to pick up their bottles and fill their own glasses.

It was a terrible scene, with the leader of Zhongyuan busy filling his own glass.

As Qing was passing the cup to his friends, a small hand gently grabbed Qing's sleeve.

"Huh? Should I sleep? I can't sleep."

"oh."

Ciyu's shoulders immediately hunched.

Since Qing, who had always done everything I asked, now firmly said no, I was wondering if I had done something terribly wrong and was looking around.

When Qing stroked Ciyu's head as if to reassure her, her stiff body seemed to relax a little.

"Why, are you curious?"

"Smell. It smells good."

Ciyu sniffs the scent again.

The Lesser Rejuvenation Pill also seemed to like this kind of refreshing, medicinal scent.

Qing's eyes flashed.

Well then, this was the time.

Qing pours a few drops of alcohol onto a spoon.

Isn't feeding alcohol to nephews with a spoon a long-standing Korean tradition and a limited opportunity that only occurs once per nephew?

Missing this opportunity would be tantamount to losing the identity of the Korean people.

"Eww."

And Ciyu satisfied Qing by giving her the reaction she had been hoping for.

"Why do you look like that?"

"It's not tasty……, it's bitter……."

"What? Alcohol doesn't taste good? I really like it. My constitution adapts to it, so it tastes like a sweet drink. Okay, let's have a drink. Thanks for coming, everyone. Um, I appreciate it, but I guess we'll have to work a little harder on our martial arts training. What? Super climax? Oh my, the alcohol was all gone. Gosh, I better drink it quickly before it tastes any better. Cheers!"

-Cheers!!!!!

There were four people sitting at the table, excluding the minors, and five if you include the temporary colleague who was kneeling among them.

But why doesn't the whole floor resonate with the loud cheers?

"Huh?"

What the heck? Is this just a free ride on someone else's toast?

For something like that, didn't you make it seem like you were all doing it together?

Even the believers who were disguised as guests could not hide their embarrassment this time.

How can you resist when the Most High was toasting?

So, I thought it would be okay if I was alone, and how could it not seem like the timing was right? It was a miraculous breath that you and I were all one.

Of course, that didn't mean that Qing found it suspicious.

How could he possibly think that all the guests except for himself were fake and that he was a group of devout followers who gathered just to have a meal without any worries?

If that's possible, then we should be concerned about mental illness or delusions, not intelligence or smarts.

Well, maybe it's a unique culture of Gansu Province or Lanzhou.

Because the regional customs in Zhongyuan were so different.

Or maybe it was a promise from Qingcheonru.

Isn't it true that the world was always pleasant when drinkers drink?

It was a problem that some races were not happy after drinking.

"Okay, drink as you please. Sit here, even though it's uninhabited. Since you've come all this way, you should take some with you."

Then, Ji Musa shed another tear.

"Ugh, how can you be so merciful……"

"No, don't you pay a monthly salary at Xuega Sanghoe? Of course, it's a high-end restaurant, but I doubt you'd be impressed by that much…"

Anyway, let's start eating.

Qing was so cute.

The little one in her arms was also wagu wagu.

Just looking at that appearance, you would think that even though the character was a bit inferior to the mother, they were still parent and child.

As always, Yi-mei reached out with her chopsticks from the steamed fish and skillfully removed the flesh, placing it on Qing's plate.

Among them, the person who eats the most politely was Pengdaesan.

And the most impertinent person was not Qingdo Ciyu, but someone else.

"Haha, hot, huff, hoosh, huff."

In fact, Xue-i's eating style was not that different from Qing-i's eating style of shoving food into her cheeks.

But the point was that Xue-i-ri was after boiling porridge or soup.

But when it's hot, don't you usually blow on it to cool it down?

Why do you put it in your mouth and try to cool it down before eating it?

Of course, that doesn't mean that Qing was the type of person who specifically criticizes other people's eating habits.

As long as it's not in a messy or unpleasant way like spitting it out after eating.

And honestly, it's nice to see you sweating profusely while making a nice sound, and it's a little embarrassing, but that embarrassment isn't mine anyway.

Just eat it and enjoy it.

That was the moment.

"Hot, whoosh, whoosh, whoosh, whoosh."

Isn't it the sound of Xue-i-ri's food-loving groaning coming from Qing's arms?

"Oh my gosh, Ciyu! What the hell was this! Oh my gosh, you have to be quiet when you eat. Who makes such obscene noises while eating? That's not good, you can't do that."

"Hot, hot, hot."

"Okay, ah. Don't spit it out. You shouldn't spit out food in front of other people. Unless it's poisoned or slightly spoiled. Okay, that's refreshing."

The long white fingers that were inserted into Ciyu's mouth were emitting a cold air.

It was a truly breathtaking scene, with the majesty of the legendary Bingbaek Shingong of the North Sea cooling the child's hot mouth.

It's such an astonishing scene that if someone saw it, they would have said, "If you're going to use the new skill like that, just give it to me."

"Be quiet. Don't make any noise while eating."

"But Mom always……"

"Mom is Mom, and Ciyu is Ciyu. That's why I tell you not to moan in front of the kids, ah."

Only then does Qing look back at Xue-i-ri.

A pitiful and sad beauty with slightly drooping eyes looks down at the table with moist eyes.

"But it's okay. Keep eating. Keep making those moaning, no, groaning sounds."

"You just said it was dirty."

"It's okay if it's dirty. I actually like it. That's part of Iri's charm. Honestly, do you look forward to it every time you eat? I think it's good. It's nice to look at and nice to hear. They say when a pretty girl does it, it becomes a painting."

The tips of Xue-i-ri's eyebrows rose and fell.

I'm kind of torn between liking this and not liking it.

She's beautiful, charming, and speaks well, but doesn't that mean she's dirty anyway?

Then, in the end, it seems like he interpreted it in a positive way, and although his voice was somewhat reduced, he started pouring hot porridge again.

It has become even more ugly because the volume has decreased.

Qing whispers in Ciyu's ear.

"You can't do that, Ciyu. Got it? Promise?"

"Promise."

"Don't just say it. Make a promise. Okay, a promise. Like this."

Qing says this and tickles Ciyu's heart.

The way of linking little fingers was a way used in Qing homeland (more precisely, it was a custom of a foreign country), and in Zhongyuan, a promise was expressed by gently placing one's hand on one's heart.

It must have been quite ticklish, as he twisted his body and let out a soft, breathless laugh.

It would be nice if you laughed and made dolphin sounds like a child.

To be honest, his eyes were a bit dull like a fish's and he has dark circles under his eyes, so he doesn't smile much in a somewhat, no, quite, no, quite gloomy mood.

"Hey."

Qing raises her glass.

It was a slightly bitter taste of alcohol.

"Excuse me, Young Lady. But may I ask you what kind of person this child is? Is it rude to ask you a question? Is it even okay for me to ask you something? I, a humble person, am at a loss for what to do. I feel deeply sorry for asking you this question…"

Musa's words, which he suddenly asks in a sly manner, were extremely cautious.

As far as I understand, the more sensitive the question, the more the ending, I don't know if you can call it ending, but it seems like it becomes longer and longer.

But it's not particularly sensitive.

Rather, if you ask a lot, wouldn't they have carried it around as if they were showing off?

In order to give Ciyu confidence, more people would be needed to ask and more people would get the answer.

"Ah. This is Ximen Ciyu. I took her in as my daughter."

"Huh!" "Huh!" "Gasp!"

Why was it that only one person asked the question, yet gasps were heard here and there?

What the heck? Isn't the drinking culture in this neighborhood a total mess? Are you just eavesdropping on other people's drinking?

But the eyes that glanced at Ciyu sparkled and were filled with affection, so I didn't say anything.

Well, if they're gathered here, they must be true fanatics who were already incapable of normal thinking.

Oh my, the Little Heavenly Demon has already served the Little Heavenly Demon Supreme Lord. Isn't this the brilliant sage god giving the world another great favor?

Rather, the exclamations of admiration were less than the surprise, as most people were so ignorant that they lost their ability to even breathe.

Anyway, it was a truly dreamlike dining experience for the top-tier fake guests.

I also reaffirm my resolve to spread far and wide this sacred supper that He has given me (or not) and to testify to this grace.
