\chapter{Bound Together (5)}

Before she knew it, a spar between Peng Daesan and Jade Dew Sword was unfolding in the yard.

Even though it was a spar, there was a difference in level, so it was closer to Peng Daesan playing along.

But I feel like the Okru Sword Borax Taoist priest keeps standing out these days.

Well, it's only natural that guests of the same age as you come here, not just the family you see every day, and keep showing up.

But I don't think that was the case in the Kunlun School.

Actually, it wasn't just her feeling.

Bengshi had been given the special mission of infiltrating, or rather joining, the Half-Sword Double-Saber Association by the Sect Leader.

In fact, a special mission wasn't even necessary.

If he had just asked Qing if there was an empty seat in the Half-Sword Double-Saber Association and asked her to include him so they could hang out together, even as just a joke, she would have gladly welcome the new member.

But, from the perspective of the old guard, with the members' faces all famous, wouldn't there be a lot of successors to Sega?

Somehow, it feels like something extremely secretive and like a large secret organization seeking some kind of profit.

Next to her, Xue-i-ri was quietly gathering her energy in the middle of a meditation, while the child was quietly being held by Jian Buxi.

Qing saw the child.

It looked like she was still and motionless, held in Yi-mei's soft embrace.

But the child's eyes were aimlessly wandering here and there, always gauging the group's reaction.

Only then does the child's appearance become fully apparent.

It looks like she's leaning back comfortably, but she's actually sitting with his upper body supported by his lower back.

The shoulders were stiff and tense, not just the shoulders, but the whole body was stiff and tense, so it seems like it's frozen like a statue.

She just kept looking around with an extremely awkward expression.

\textit{Why didn't I notice?}

Then the child's eyes meet Qing's.

For some reason, a small sense of relief settled in those unusually dark, lusterless, pitch-black eyes.

\textit{I don't know why, but it was clear that the child felt an unknown closeness to me.}

\textit{Maybe there was some kind of connection at that moment when the child's past was revealed when she was rescued.}

\textit{Or maybe she also feels some kind of kinship with me because she was connected to the lonely star who has no friends.}

Or maybe it was because she felt comfortable sleeping in her arms last night, but Qing couldn't quite figure out why.

Well, it's a thousand, ten thousand times better than being completely cautious.

Qing smiles brightly and sits down next to Jian Buxi.

The light weight of the child who only reached out and hugged her when Qing opened her arms.

Qing said quietly, holding the child in her arms.

"From now on, your name is Ciyu\footnote{Jayeo in the original text}."

The child's body flinched.

Qing skillfully drew her sword with one hand, stretches out her hand, and carved letters into the dirt under the porch with a strong stroke.

西門慈與.

"This is the character 慈(ci), which means to like or love. This is the character 與(yu), which is used to say to give or to be together."

The child stared blankly down at the letters.

Qing, who was feeling a bit embarrassed, buried her head in the child's ear and whispered.

'I wish you are a loved one.'

'But there's no such thing as a free lunch. If you really want to be specific, there are, but whatever.'

'It would be better if you could like others first rather than having others like you first.'

Qing tapped the yu character in the name.

It was a character that has both the meaning of giving and the meaning of being together.

Because whatever you give out will eventually come back to you in some amount.

Some will return more affection than they gave, while others will only return a portion after charging a vicious fee.

But in order to be together, you have to give.

To become us, not me.

"Of course, those bastards are an exception. Those who don't behave like humans don't deserve to be treated like humans."

The child did not answer and just continued to stare blankly at the letters.

"Why, you don't like it?"

Then, dori dori. The child's beautiful hair tickles Qing's cheek.

"What? It's not that you don't like it, but it's not that you like it either."

Dori dori.

Qing asked again, giggling.

"Well, do you like it?"

Only then did Ja-yeo nod her head.

"Do you know who I am? I am the Heavenly Blossom Sword, Ximen Qing. Heavenly Blossom Sword is a nickname given to me by people out of respect for my greatness. Ximen is my family name, and Qing is my given name. Do you know what this means?"

Dori dori.

Qing strokes Ciyu's head.

"Ximen Ciyu. From now on, if someone asks you your name, just answer proudly like that."

Then, a very faint murmur came faintly into my ear.

"Ximen."

"omg."

What? You said it? You knew how to speak?

Well, it has a mouth.

And of course, since you understand what Qing says, you can speak too.

The child's first word was a preface.

There would be no reason to suddenly go to the west gate of the temple, so what the child said was probably just a way to say my surname.

Because the surname was more precious to the child than the name I received, I wanted it even more.

because.

"You're Mom?"

He makes a groaning sound.

Fortunately, it didn't happen like it did with the cheap guy, but it still gives me goosebumps.

"Hmm. It's bearable, but, um, I'll have to think about that a bit."

Then the child's shoulders slumped.

\textit{Master said that it was just a test for Master Wunue, and that she had originally planned to take Ciyu to the Divine Maiden Sect.}

\textit{But if you think about it, it's all my fault in the end.}

\textit{Master acccepted me even though I am a Heavenly Slaughtering Star, and I have become such a proud disciple to Master, so Master are also accepting her even though she's an artificial Heavenly Slaughtering Star.}

\textit{And didn't I already said this in front of Monk Wunue?}

\textit{I will take care of it. I will take responsibility.}

\textit{But that was just my intention to receive her as a disciple, just like Master had done for me.}

\textit{However, she's so happy to have received a family name rather than a new name, and she's so happy that she thought I am her mother before I even say anything, so I feel awkward asking her to be my disciple instead of my child.}

\textit{If you think about it, the two aren't that different.}

\textit{She was a child who was locked in a small room, shown everything in the world she didn't have, and instilled hatred in her heart.}

\textit{If the thing that Ciyu wanted most was parents, well, there's nothing I can do about it.}

"Mom won't do. I'll be the dad instead."

Then Ciyu nodded.

Fortunately, Ciyu was an open-minded person who didn't care about gender as long as she had a mom or a dad!

But.

"What about Mom?"

"Do you really need your Mom to feel better?"

Nodding.

\textit{Well, then, what?}

"Yi-mei? Do you want to be her Mom?"

"Ung, I am the aunt."

It meant that it was not the case with Jian Buxi.

"What? You want to be the aunt? Isn't that a cheap trick? You don't want to take responsibility for the child, but you want to pamper her as much as you want as an aunt? What an irresponsible pleasure."

"Ung, Xiao-mei and I are already family. You can't marry with family."

"Hmm. You're bringing up the issue of kinship here."

Anyway, Qing had nothing to say, so she passed it off.

If the family tree gets tangled, it's a big problem, you know.

Qing turned her head to the other side.

"Do you want to be the Mom?"

"Why are you picking on her mom like you're picking her a snack? And why are you the dad?"

Before he knew it, Qing was looking at Peng Daesan who became dumbfounded.

Next to him, there was Bengshi who was so moved that he was shedding tears, covering his mouth as if he was on the verge of sobbing.

Qing laughed at him.

"Because I intend to raise Ziyeo very strongly. I'm the epitome of strictness, and I need to show Ciyu a father who will shape her entire life with instilling discipline. So, Mom has to take on the role of accommodating her whims. It's called the good, um, good-grape-bad-grape strategy."

"Do you usually say that so openly? And what exactly a good and bad grapes—"

"Well. If you don't tell me, I won't know. Later, when Ciyu starts rebelling, she might ask what on earth Dad even did for her. But look, Ciyu. I'm working so hard to find Ciyu a mother. Isn't that amazing?"

As the child nodded, Peng Daesan looked astonished.

Well, anyway.

"So, Iri? Want to become Mom?"

"I'm not confident. I have no experience…"

"Does anyone have any experience from the start? Hmm. Then what should I do? I'll have to ask Lan-Ah. But since she's in Sichuan, um, should Ciyu go see Mom?"

"…But I'll try."

As soon as Qing brought the word 'Lan-Ah' to her mouth, Xue-i-ri change her words.

Qing giggles and strokes Ciyu's head.

"That's great. Now Ciyu have a mom. How do you like it? Do you like it?"

Ciyu gazed intently at Xue-i-ri.

It was a moment when Xue-i-ri swallowed hard and showed a nervous expression for the first time in a while.

Ciyu's head was tilted.

Unfortunately, it looks like she didn't like it.

"Oh, but the laws of Heaven doesn't change just because you like them or not. Even though Iri is somewhat weak, her martial arts skills are lacking, and her only advantage is her pretty face, there's nothing you can do about it."

Ciyu's shoulders slumped again.

Xue-i-ri's shoulders also slumped.

\textit{Even if she's just an artificial Heavenly Slaughter, it seems that a Heavenly Slaughter doesn't get called that for nothing, isn't it? Isn't this a scary little kid who openly stabs your heart in the face right in front of you?}\footnote{Oh the irony}

Qing giggled and soothed Ciyu.

"It's okay. You might like the next mom."

At that moment, Ciyu's head lit up.

The child looked up from her arms had eyes full of questions, so Qing explained.

"In Zhongyuan, the more mothers, the better, right? Successful kids tend to have seven mothers. Ciyu can't afford to be left behind."

It was said that a hero was a man of three wives and four concubines.

That means, if you were the child of a hero, you need to have at least seven mothers to be worthy of being a child!

Even in a commoner family, there should be at least three people, so even if you sleep together, the child won't go somewhere and fell off the bed.

\textit{Let's see, if I add Lan-ah, Young Lady Murong and Young Lady Gongson, there are four of them.}

\textit{If there are four mothers, no matter where she go, she won't hear anyone say that she don't have a mother.}

And it's necessary for everyone.

If there was only one mother, Xue-i-ri, then Snow Flower will suddenly become a widow with a child.

But what if all the female members of Half-Sword Double-Saber Association were mothers?

At that time, it will be passed over as Heavenly Blossom Sword and her friends taking care of the child and raising her.

It's a good thing for the children who needed their mothers right now, and as they get older, they will naturally come to understand what's going on.

"Child, come here."

Xue-i-ri stretched out her arm to Ciyu with a somewhat serious expression.

However, Ciyu clearly expressed her intention to not go.

"Hurry."

But Xue-i-ri was resolute.

\textit{Somehow, the maternal dignity was already evident, so I think she will become a strict mother to her children in the future.}

\textit{You said you were unsure, but surprisingly? Quite a bit? You have a thing more useful than just looks?}

As Qing gently pushed her, Ciyu finally moved to her new mother's arms, which she doesn't like.

Then, Xue-i-ri hugged Ciyu tightly and whispered in a determined voice.

"Remember, I'm the First Mom. First, you understand? Yes. Other moms are fine, but if you happen to have a mother with Tang surname later, she's definitely ranked below me—"

Qing immediately snatched Ciyu back.

\textit{This Mom is no good.}
