\chapter{Bound Together (3)}

Wunue smiles brightly and says.

"My dear, I feel sorry for you. I've already felt your true nature, so you can just assume it was just a grumpy old man throwing a tantrum. But I really wanted to be sure there was hope for that child. When I was young, I felt like I could do anything, but now, perhaps because I have so much, fear takes over, and I've grown old. Anyway, your teacher was so confident."

"What useless talk you old monk."

The atmosphere seemed to be moving along amicably, but soon new news arrived.

-Senior, the Giant Tower Emperor has awakened.

There was news that Emperor Geotap, who had been beaten so badly that he lost consciousness, had opened his eyes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Emperor Geotap had a surprisingly calm expression.

\textit{It's truly an eyesore to see him acting so detached and dignified like a monk after being beaten like a dog and having his dantian shattered.}

\textit{If I had my way, I would have hit him at least once, but I can't do that because the elders were here.}

But Amukhaprap was able to do it.

"Your mother and father have been replaced by this."

Swish! Suddenly, a strong smell hits them.

It was Amukhaprap, holding a chamber pot that they had no idea where it came from, and breathing heavily.

Well, since Amukhaprap was a lama from Hyeolryeumsa, it wouldn't have been difficult for him to pick up a well-rotted chamber pot somewhere.

Monk Wunue clicked his tongue.

"Oh, this guy."

"This bastard is a rotten piece of human flesh, so rotten to the core that the stench was unbearable. I had no choice but to pour something cleaner on him. A rotten smell is better than him."

The Giant Pagoda Emperor, who was covered in urine, or was tied to a thick pillar in a Buddhist temple with his arms and legs tied tightly, unable to wipe it off, just crumpled his face with a look of disgust.

Then, when faced with those disgusting looks, wouldn't you suddenly force a smile?

It's an attitude that says I will never show you anything that you find refreshing.

Could it be said that it was a truly poisonous attempt?

"Kuuuuu, you guys- Whew, Whew, Whew, Whew!"

Although he tried to act dignified, the Emperor of the Tower who opened his mouth for no reason, retched violently, and vomitted his stomach's content.

When everyone's gaze was filled with a mixture of disgust and pity, only then did the Giant Pagoda Emperor, with his miserable appearance, let out a laugh that made it seem like he was laughing again.

"Haha, yes, laugh all you want. But you won't hear anything from me. Yes, this wretched body may one day submit to you. But not now!"

And then he stuck his tongue out and, bang!

The severed tongue rolls on the floor, and blood gushes out, wetting the Emperor's chin.

What was remarkable was the expression on the face of the Giant Pagoda Emperor, who was glaring with a faint smile as if to say, 'What you're going to do?'

'Someday, whether through torture or persuasion, I will inevitably telling the truth, so before that, I chose to cut off my tongue and become mute.'

You could say it's a truly arrogant attitude.

However, it was a rather hasty decision.

"You, you son of a bitch, abandon us, how could you! Was that what Podalap meant? To use and discard as you see fit…!"

The basis of interrogation was a three-way meeting.

The lamas of the Blood Thunder Temple, who were being dragged in tied up, became enraged and rushed at Emperor Geotap, but were stopped by ropes.

But what's with that appearance? Have you been unable to sleep?

They all have dark circles hanging down their faces, as if they have dark circles under their eyes, giving them a hazy appearance.

Of course, since the unmanned unit had lost its dantian, it was impossible for them to sleep soundly and peacefully, but even so, everyone's condition was not ideal.

The Giant Pagoda Emperor opens his eyes wide.

No matter how much I thought about it, there was no reason for the lamas to be hostile to me.

Rather, as someone who shares the same cause, he will have something to feel when he sees his own severed tongue.

As comrades who share the same ideals, even if they cannot make the decision to cut off their tongues like I did, I will not bow down to those Zhongyuan bastards.

There was such a belief.

And at Runrin's words that followed, the Giant Tower Emperor realized that something was seriously wrong.

"That bastard offered us up as a sacrifice to the law. Because of that, we…"

Crack! Teeth clash, a sound filled with hate.

But for a moment, he suddenly became as if he was begging, as if his feathers were standing on end and he was showing goosebumps like a plucked chicken.

"Look here, look here, what was that formation, what was that formation? Why does it never end? What on earth do I do, in this nightmare, huh? No, it can't be?"

Runlin started to squirm, then suddenly fell to the floor and started banging his head.

It's not a show, it's a really ferocious look that makes you want to break your head.

"Yeah, it's not a dream. It's not a dream. Whoa, listen, what kind of formation was that? What kind of formation was it?"

It was a heartfelt and earnest question.

Nan-Gong Daero clicks his tongue and answers in a cold voice.

"It's the Blood Cult's evil method. It's a terrible annihilation that requires the lives of three thousand people to be created. It's an annihilation that uses the power of a thousand lives to trap you in a horrific illusion. It looks like that evil servant of the Blood Cult was trying to silence you by killing you too. Well, he's so vicious that he'd cut off his own tongue, so he wouldn't mind taking someone else's life."

"Ah! Aaaah, ugh, gulp!"

Gagging?

Why would I want to harm the virtuous monks of the prefecture?

Even though Emperor Geotap tried to deny it later, it was not like a tongue that had already been cut off would grow back.

Rather, the tongue root, which was finally bleeding, started spewing blood again, and the sight became even more ugly as the blood that had gone down the nose while coughing loudly flowed out.

Nevertheless, Emperor Geotap shouts with all his might.

It's a conspiracy, it's a conspiracy! It's a conspiracy!

Actually, it was true that it was a conspiracy.

This was how it is. Is this the way things are?

Because the real culprit was someone else.

However, the only ones who knew that Qing had imprisoned the lamas in the dharma were Qing, Ai, and a friendless, lonely star whose existence was uncertain.

"Tongue, Blood Cult? Are you talking about those evil human scum? No way, no way, no way!?"

"There's evidence. They captured the Blood Cult's monsters in that spacious building over there. Hmm. No, really. Are you the ones who didn't know? Unless the Blood Thunder Cult, the Blood Cult, and the Blood Cult members were colluding—"

"Nonsense! Forty years ago, when the Blood Cult rose up, we, the Blood Thunder Clan, also helped punish those evildoers! Even if we hate you oppressors of Zhongyuan, how can we join hands with monsters who have abandoned the laws of nature?"

"I don't know. Whether that guy was a Blood Cultist, or whether Podalap has joined forces with the Blood Cult. But isn't it the case that an upright person wouldn't cut out their own tongue to silence someone?"

Nan-Gong Daero points to the feet of the Heavenly Emperor, who was still screaming and shouting, with his sword still in his hand, and the fragments of his tongue lying scattered underneath.

At that, Runlin's mouth fell open.

And then, as if in disbelief, his trembling eyes turn to the Giant Pagoda Emperor.

"Is this, was this true? Are you really saying that the Emperor, you, no, you were a lackey of the Blood Cult? That's, no, no. It's definitely Gelwa Rinpoche in Podalap. Heh, heh, heh, I see. He joined hands with the Blood Cult in Podalap."

The way the honorifics, common courtesy, and deference were constantly mixed up from earlier clearly reflects the confusion of the lama monk.

"Aya, Aian Aya!"

The tongueless Giant Tower Emperor desperately shakes his head and screams.

There must be no rumors that Podalap has joined hands with the Blood Cult.

Are you planning to throw the long-cherished wish of the nation into the trash can?

That's not it.

Blood sect was just a means, like a tool to be wielded. Do you judge whether the sword was dirty or clean when used?

Once the dirty black thing was no longer useful, just throw it away.

The true cause was something else, so the future we dream of was not like that.

It's not the ugly collusion you think it is.

But people only truly understand the meaning of something, whether it be through words or writing, after they have made contact.

It's too early to cut off the tongue.

But what can I do?

That doesn't mean that a cut tongue won't grow back or reattach.

The lamas were just full of hatred.

That was when.

"[Who were you blaming now, you vile thing? Didn't you slaughter countless innocent people simply because they adopted the customs of Zhongyuan? Those who were resentful will already curse and oppress you. How were you any different from the Blood Cult, who do not even know that they were being manipulated by others and who do not regard others as human beings?]"

"[We've already paid the price! What do you know! We've already, already…]"

Runlin's shoulders slump.

"If there's anything I can do to help, I'll do it. However, since it seems I haven't yet escaped the evil grip of the Blood Cult, I'll do it on the condition that you find a way to break free from it."

In Qing's opinion, these kids still haven't come to their senses.

Even in this situation, I'm still holding on to my own safety. Well, it's because they're these guys that they would do such inhuman things without hesitation.

After all, the people, the liberation of Qinghae, and my own safety were the most important things to them. So, would those who claimed to be protecting the people have gone around massacring the villages of the Jang tribe?

The high-ranking officials of the Jeongpa faction were looking at the serious Tian Feizi.

How long has it been since the end of the law and you're still talking nonsense?

Was there anything in the Blood Sect's formation that we didn't know? It couldn't have been more advanced, right?

What does this mean? Do you know anything?

It was the gaze of Wunue, Ximen Surin, and Nan-Gongdaero.

The wise man shook his head seriously and sent his answer.

Why were you asking me that?

That's the end of the interrogation.

The interrogation ended without providing any significant information about the blood sect.

But it was also an interrogation that yielded sufficient harvest.

To begin with, there was no information that the Blood Thunder Cult was related to the Blood Cult, so instead, didn't they realize that the Blood Cult was secretly active in the West and had reached the West's first person?

Perhaps the rulers of the West, their clutches may even extend to Podalap.

Since then, the conversation has turned to politics.

After cutting off the veins of the Giant Pagoda, he was transported to Shaolin's Repentance Hall for safekeeping.

Because he was a person, and also a big shot who can be entangled in the machinations of the blood cult.

Among the repentance halls, the most notorious was the repentance hall of Shaolin.

The sinners of the Blood Thunder Cult, including Runlin, will later confess their atrocities in the city of Qinghae and testify that Podalap joined hands with the Blood Cult.

It doesn't matter whether you actually held hands or not.

The fact that the lamas themselves testified was important.

Whether or not they actually held hands, Podalap has no choice but to deny it, so they won't be able to make any nonsense for the time being.

And in return for handing over the criminal to the Jeongpa, Amukhaprap will receive support for the reconstruction of Hyulroeumsa.

There were no disciples left, so it was an urgent situation where we need to fill the gap immediately, so we need elixirs and martial arts instructors to train them right away.

You might ask why the political party was helping and then losing again?

In fact, this was actually a huge advantage.

Wouldn't the entire Zhongyuan know that the Wulin Alliance helped rebuild the Blood Thunder Temple?

From now on, unless there was a unilateral mistake on the part of the Maeng, the Blood Thunder Demon will never be able to be hostile to the Wulin Alliance.

Because the whole world will point fingers at you and say you were truly ungrateful.

Even if that weren't the case, the instructors of the Wulin Alliance would help train their disciples, so that connection alone would be invaluable.

Because it was a relationship with those who will lead the sect by taking on a central role as the greatest disciple of the Blood Thunder Sword Master.

but.

"Are you okay? Even I wanted to beat all those kids to death."

"You are brave woman, but the reconstruction of the Blood Thunder Temple is more precious than own grudge."

The reconstruction of the Blood Thunder Shrine was more important than personal grudges.

\textit{If only his Zhongyuan wasn't so weird, he'd look like a pretty decent monk. Well, I guess he's called a weird monk for a reason.}

"Yes. You, valiant one, now was the time to make an offer you cannot refuse. If you, valiant one, take refuge now, you will be offered the opportunity to become a teacher of the Vajrayana."

"Is that right? And come to think of it, I haven't seen any nuns among the lamas. Is it like Shaolin Temple, not accepting women?"

"The precepts of a monk do not come from India. However, you, the virtuous one, are a Zhongyuan. We, a mature people who respect practitioners regardless of whether they were Indian or Zhongyuan Buddhas, have no problem with your actions. Rather, you, the virtuous one, can bestow the precepts on the women of Xizang."

If you listen to it from the beginning, it's the sound of foaming water.

Isn't it true that Buddhism in Xizang was in a situation where it cannot raise its own nuns because it does not have an order of nuns?

It was a roundabout way to say that he would make Qing the founder of the Order of Bhikkhuni.

In other words, he was saying that he would now completely cut off ties with the Potala Palace.

Could it be said that it was an ambition to establish a new Qinghai Buddhism for Qinghai people?

But Qing didn't know that.

Of course, there's no way to know.

If she didn't even believe in Zhongyuan Buddhism, how would she knew the circumstances of Xizang Buddhism?

So what was Qing's impression?

\textit{Wow, you're really persistent and tenacious.}