\chapter{Bound Together (12)}

Qing was comfortable.

Another day passed that seemed like a dream to the new believers in Lanzhou.

Word of the banquet held (or was held) for the believers last night has already spread far and wide.

Those who were unable to attend were merely able to confirm that the Heavenly Demon Lord was well within reach.

Nevertheless, the believers felt at ease and their worries and concerns disappeared, so they expressed their gratitude and prayed for the peace of their bodies and the development of the new religion.

This was the joy of believing in a real God.

In terms of finding solace in the mind, wouldn't it be more likely to find some kind of comfort by worshipping a living person rather than a non-existent being?

(only when the target does not request property)

In that respect, the Cheonmasingyo religion can be said to be quite practical and rational.

So, the group had a quick breakfast and then boarded the carriage.

But why aren't there many people in the morning?

It's time to prepare for spring and sow seeds again, so it's not the time to be idle like in the middle of winter.

Even so, it wasn't a time when there was enough work to have people from all over the city come out onto the streets in the morning.

Surprisingly, these were not ordinary people.

They were truly true demon cultists!

Perhaps the disciples were hoping that they could win the favor and eat lunch and dinner together like they had heard about today, but why did they leave?

Even from afar, it was a vague feeling of wanting to come out onto the street to catch a glimpse of that back view.

Qing thinks, um, he came out to see me, but this guy's face, it's too pretty, that's the problem. It needs to be a little bit pretty.

This was not the kind of self-indulgence that was spoken of in the hometown of Qing.

Because it was true and sincere.

Your face must be pretty.

What good was my pretty face?

Isn't it really useless other than having fun every time you look in the mirror?

Of course, that's not the case.

Just having a pretty face makes life seem less difficult, and wouldn't people's basic reaction be to show favor?

Compared to when I was a beggar, I would spit, curse, and turn my head away, it's a world of difference.

While the believers were enthusiastically sending him off in their hearts, Qing left Lanzhou.

The goal was common property.

Kongtongsan was a long mountain range that rises north to south and serves as the border between Gansu and Shaanxi provinces from Lanzhou to the west.

That is, it meant that there was a well-maintained road leading to Shaanxi, so it was easy to take a carriage until the foot of Kongtongsan Mountain appeared.

Besides, a skilled groom-

Rattling!

-Oh no! Sorry! There's a rock on the side of the road!

An apology, almost a scream, flew from the stable.

A familiar voice, you must be Musa, having just changed your last name last night.

I was a skilled man who, thinking this was the right time, volunteered to be his assistant and successfully snatched away the glorious mission of escorting him to Kongtongsan.

As soon as Qing thought about it, he stepped on a stone and was killed.

But if he really lacked the skill to drive a carriage, he would not have dared to volunteer for fear of causing inconvenience, regardless of the honor.

In fact, I don't remember ever driving a carriage with more concentration than I do now.

This was a true human-to-human system, or a system of human-to-horse, that focuses on providing the best possible riding experience.

So, it was a comfortable eight-day journey westward, passing through Jeongseo-hyeon, Hoejeo-hyeon, and Yungdeok-hyeon.

During that time, Ciyu memorized a total of four letters.

It was a mysterious memory ability where if you taught him three letters a day, he would memorize them and then forget them the next day.

It was the moment when the grand plan of learning the Thousand Character Classic by reading three characters a day and taking a year to complete it all came crashing down.

Yeah, where's one letter every two days?

If you have 500 characters in 1,000 days, and complete the Thousand Character Classic in 6 years, well, Hmm. I guess I'm a bit illiterate.

Still, should we be thankful that we can memorize easy letters?

One, two, three, seven, eight, eight, mouth, ten.

But I can't type this in words.

So, if I were to say the letters that were truly letters, they would be Ximenja Yeo Su Rin Gyeon Po Hee, and then Qing, the last letter I memorized after my name. That's all for ten letters.

But when I think about it, when I memorized my name, I spent the whole day mumbling and writing it down.

Our daughter was such a fiery filial daughter.

But why can't Xue-i-ri memorize it?

Even though she knows how to write her own name, Xue-i-ri keeps forgetting it.

I guess it's because Gunyeong was such an unattractive mother.

Anyway, so Yongdeok-hyeon.

It was not a public mountain… …but a small town nestled at the foot of Yukdansan Mountain.

And the mountainside behind Yukdansan was Kongtongsan and Kongtong Sect.

Originally, to reach Kongtongsan Mountain by carriage alone, one had to take a detour north and come up from Shaanxi Province.

But, aren't only the experts and those who were not experts but useful among the lower ranks gathered here?

There was no need to turn back, leaving behind a strong bridge, which meant that Ji Musa's happy times would end here.

"Oh, dear lady, please live long and healthy. If you would allow me to consider it an honor to remember that a humble person like you always wishes for your bright future, I would be happy for the rest of my life."

It was a very heavy farewell somehow.

But if he wants to be happy for the rest of his life, he can't help but say a word to Musa, who has been working hard for him by volunteering to run all kinds of errands as a groom.

"Thank you for your hard work. I will never forget the kindness you showed me, Master Ji."

"Ugh, ugh, ugh."

Ji Musa was moved and covers his mouth.

My eyes were red and I feel like I'm going to burst into tears, but I wonder if this was really that moving.

It was said that long, long ago, there lived a sage with very, very high magical powers in Kongtongsan Mountain.

This sage's name was Gwangseongja.

It was said that the power of Gwangseongja was so great that even Emperor Gongsun Xuanyuan, the ruler of the world at the time and a god who ruled over humans for fun, respected Gwangseongja and sought his teachings on self-cultivation.

Who was Gongsun Xianyuan?

He was a demigod who was considered the progenitor of the nation, similar to Dangun in Qing hometown.

Even Gongsun Xuanyuan was such a great sage that he had to seek teachings from others. You can't even imagine how noble a person he was.

Therefore, Kongtong Sect was considered one of the birthplaces of Taoism and was a sacred mountain of Taoism.

Of course, it was just a tale that some people believe in, as it was still nearly a thousand years before Laozi, the founder of Taoism, was born.

So the people of Zhongyuan called Kongtongsan the most famous mountain in Taoism.

And the common faction that established itself above them was the one that took pride in being the most authentic Taoist sect.

Of course, it was also necessary to hear the opinions of other Taoist sects.

The Kunlun School claims that they were Kunlun itself, and that the Taoism that originated in the land of the Taoists was the most authentic.

Qingseongpa was located in the birthplace of Cheonsado and has inherited its spirit. Above all, as the oldest Taoist school in Zhongyuan, we claim that our Taoism was the most authentic.

The Jongnam faction claims that we were the most orthodox Taoist faction because we were the direct successors of the Jeonjin faction and had a great influence on the Hwasan faction, the Wudang faction, and Qingseong faction.

That's why when the volcano and the shaman come up with an authentic story, they tend to change the subject.

However, they all agreed that Kongtongsan was the most famous mountain in Taoism.

Even without that, it was one of the most famous mountains in Zhongyuan.

Kongtongsan Mountain, with its exquisite harmony of the rugged cliffs of Bukak and the graceful trees of Namak, was said to contain all the beauty of the mountains of the central plains.

So the back door of the common area.

A person's shadow falls behind the fiery sunset hanging on the mountainside at sunset.

Myunseon, the fellow disciple, quietly watches the scene with his hand on the sword hilt.

The west side of the Kongtong Sect was not only a mountainous area with rugged terrain, but it was also a remote area with few visitors, with another mountain nearby.

Even now that the sun was setting, those coming from the west were merely seen as pitch-black shadows in the dazzling sunset.

It was natural for Myeonseon to fiddle with the hilt of his sword, wondering whether he should ring the bell or not.

And finally, when the unidentified figures were close enough to be seen through the obstruction of the setting sun.

Myeonseon immediately recognized Qing and his party.

Of course, there was no one in the old school who cannot recognize the face of Bingseolhwa in Heavenly Blossom Sword.

Qingdo Myeonseon's face looked somehow familiar.

I don't know the name, but I think I've seen it somewhere, but if you look closely at the warriors of the Old Gate School, there's only one place worth seeing.

"Hello? Um, I think we met at the Yongbong branch, correct?"

"Oh, you remember me, even though I only greeted you once. Aren't you Lady Ximen? Why were you coming at this hour, and through the back door at that?"

"Oh, I stopped by on my way back from Kunlun Sect on business."

"Ah, were you coming from Gansu? The terrain was rugged, and you must be tired. I'd like to take you to the guest house right away, but guarding the back gate was dangerous, so I can't. Please wait a moment. I'll send a signal."

Myeonseon greeted Qing politely.

That was understandable, because the scene at the Yongbong branch, the question about how the distribution would be, was still fresh in my mind.

Myeonseon takes out a strangely shaped stick from his back and taps it.

I don't know what it's used for, but it seems to be some kind of traditional Chinese percussion instrument that makes a very loud thumping sound.

Of course, it wasn't a musical instrument, but a type of weapon called a trumpet.

As I waited like that for a moment, the unmanned aerial vehicle flew with a swift movement and landed.

"Oh, isn't it Daesan? Still traveling, huh? How was Lady Ximen? Lady Xue was here too. No, this was it."

The joint-armed unmanned unit patted Peng Daesan's shoulder with a smug expression.

Peng Daesan lets out a deep sigh.

"I know what you're thinking. Done. It's not the picture you're thinking of."

The reason for mentioning the name was obvious.

Listen carefully.

Miss, what was this person's name?

I know your face, and I've heard your name.

Changbin was my friend, but I can't call him Changbin's friend.

Because he looked like he was thinking hard, trying to recall something with a face that seemed to know something but not know it.

I noticed this and let you know.

"Ah, Master Myeonak. It's been a while."

"Haha, how are you, Heavenly Blossom Sword? By the way, who is the pretty little fairy over there? Hello? My name was Myeonak."

Myeon-ak says this and waves his hand to Ciyu.

Then, as if embarrassed, Ciyu buried her face in Qing's arms.

"Oh, this is Ximen Ciyu, I took her in as my daughter. And this is my Sworn Sister, Jian Buxi."

"Ah."

Myeonak paused.

But that was only for a moment.

Myeon-ak, who immediately guessed that the child had a strange story, quickly changed the subject.

"No, isn't this the dawn of the Eight Great Embodiments of the Martial Arts? Two more peerless beauties I didn't know about have appeared. "Come on, come on. You must have been tired from climbing the mountain. First, unpack your bags at the guesthouse."

He was a very sociable man.

However, Peng Daesan didn't look particularly happy, but then again, he didn't have any friends.

Anyway, Ximen-Qing arrived at Kongtong Sect.
