\chapter{Bound Together (7)}

One of the characteristics of a person who was bad at studying.

Prepare thoroughly before studying.

First, I diligently create a daily schedule that I have no intention of keeping.

Also get good textbooks and teaching materials.

They give money to the lectures that were said to be good.

Also, I need to find a house around there.

And when I actually try to study, I suddenly get a case of obsessive-compulsive disorder, so I wash and clean thoroughly to drive away evil spirits and calm my body and mind. Then, I suddenly wonder why cleaning was so fun, and do I have a talent for cleaning?

The same thing happens not only with studying, but also when you start a hobby that you have no particular interest in but that others find interesting.

Not surprisingly, Qing also had a past like that, so where on earth did that habit go?

"Master, is Depilation-and-Marrow-Cleansing\footnote{伐毛洗髓; Famaoxisui; lit. 'cut hair wash marrow'} a difficult task? I'm a seasoned expert now. Shouldn't I be able to do it?"

Depilation-and-Marrow-Cleansing!

In the past, there was a legendary immortal named Dongfang Shuo who had the wonderful nickname of Mancheon.

They say he lived for three thousand years or something.

When Dongfang Shuo was nine thousand years old, he met an old man and said to him in a proud tone.

'Hey kid, how old are you?

'What? Ninety years old? Wow, you're such a baby, baby.'

'Child, sit here for a bit.'

'I'll tell you the secret to my longevity.'

'I have lived for nine thousand years, practicing strict vegetarianism and accepting the energy of nature.'

'Every three thousand years, the bones were pulled out and the marrow washed out (返骨洗髓; Bao Pi Fa Mao), and once every two thousand years, the skin was shed and the hair was replaced with new hair (剝皮伐毛; Fan Gu Xi Sui).'

The old man with yellow eyebrows who heard Dongbangsak's words must have been so shocked that he could have ascended to heaven.

A young man with a fresh face suddenly starts talking informally and says that he has lived for nine thousand years.

But, as the times were what they were, there were quite a few people who had lost their minds due to the long war.

The old man looked at him with pity, thinking he was a crazy person.

Well, they say you quit eating food with fire.

Giving up on meat meant not eating meat, and even if you did eat grains, you didn't cook them over fire.

He was a true example of strict vegetarianism, thinking that rather than living for nine thousand years, he would rather eat grilled meat and die when he was a hundred years old.

Or maybe that's why I'm crazy.

anyway.

Here, the word that combines the words 'Fan Gu Xi Sui' and 'Bao Pi Fa Mao' was 'Fa Mao Xi Sui'. Depilation-and-Marrow-Cleansing.

And for martial artists, the Depilation-and-Marrow-Cleansing method was a real technique.

The subject of the procedure must be young and have not yet hardened their bones or blood vessels.

The practitioner must be a great master of Qigong who can use the movements of the body with great freedom.

This was a technique in which the practitioner inserts energy into the subject's meridian to remove turbid energy and open up blocked blood.

Or in modern terms, it was cleaning the energy veins with high-pressure jet wash.

The effect was incredible.

I was barely able to circulate my internal energy through the blocked blood vessels, and I was building up my strength while struggling.

Push your energy into your dantian with every breath of your breath, through the blood vessels that were well-opened without any obstructions.

The difference in learning speed between a child who received a Depilation-and-Marrow-Cleansing and a child who did not was like the difference between a rabbit and a turtle.

It was also a technique that Qing wanted to perform on Ciyu before teaching her martial arts.

Of course, Qing didn't know the details.

Because she's Qing.

But, they said it's incredibly good.

There were laments that she heard even during my wandering days, and even now, if she sat in a guesthouse and listen carefully, she could easily hear them.

'Ha, this unfair world, if only I had learned martial art after receiving the Depilation-and-Marrow-Cleansing, I would have been known as a peerless master by now.'

Ximen Surin looked at her.

"Disciple's Qi reserve has already surpassed the realm of masters, and your mastery of various Qi Cultivation Art has reached a state of maturity, so it is only natural that you could do it. It is not as difficult as you might think, but it is also challenging."

Ximen Surin knew Qing well.

She's sure her disciple was not asking that with proper knowledge.

So, Ximen Surin explained the dangers of Depilation-and-Marrow-Cleansing.

The Depilation-and-Marrow-Cleansing method was not that difficult.

Even the storytellers say that the protagonist's teacher must have opened the protagonist's Imdokyang vein before he dies.

The principle was the same, except that the main character was already a grown man.

It's something a dying teacher would do.

But it was also a difficult technique.

After performing a Depilation-and-Marrow-Cleansing ritual, the practitioner would permanently lose a significant amount of Innate Qi, and in the process, his or her own vitality and spirit would be damaged, often leading to serious illness.

That was the reason why the teachers in the stories died with a happy smile.

In fact, for this reason, the Depilation-and-Marrow-Cleansing was a great benefit that only the disciples of the noble families can receive.

Because in most cases, elders who have already stepped down from the front lines were stepping forward for the future of the family.

This was also the strength of the famous family.

This was why in sects with a long history and great influence, talented people grow up with a spoon in their mouths and become masters.

The Five Great Families of the past remained The Five Great Families of the present, and would still remain The Five Great Families in the future.

"Ah, they say there was no such thing as a free lunch."

Of course, Qing didn't know about the aftereffects of the Depilation-and-Marrow-Cleansing treatment. It was only natural, since she was Qing.

But even if she knew, it was the same.

"Being sick is this disciple's specialty, isn't it? Hehe. I guess I'll just have to suffer for a bit."

Ximen Surin's eyebrows twitched.

However, the movement of the anger bar was minimal.

It was so bizarre that it was easy to say that you will lie down sick in front of your teacher, so it was appropriate to be punished by heaven, or rather, by nuclear punishment.

She was so proud of her disciple who willingly agreed to do it without any hesitation, as if there was no reason to worry, for the sake of her adopted daughter, who she wondered if she was still attached to.

So she could only sighed deeply.

"I've always been concerned about the things I haven't been able to do for Disciple. Isn't that what an old warriors should do for their disciple? Bring the child."

"Oh. No, Master. How could a disciple do such an unfilial act? My Qi is so abundant, and you know I'm strong."

"Disciple is really underestimating her master. The difference between the martial artist of the Profound Realm and Unrestrained Realm is evident from the very moment they perform their actions. Therefore, the Internal Qi and Innate Qi consumed are significantly reduced. Since I can use only a small amount, why should you pay such a high price?"

"Since the value of an item varies from person to person, wouldn't it be fair to say that a trade is established if a transaction took place? For me, Master's health is more precious than anything else, so it could be said that I'd pay an even higher price if you do it."

Ximen Surin thought about it.

\textit{I thought she would throw a tantrum, but the disciple's argument is very plausible, so it seems like the thief was really good at teaching.}

\textit{And I feel happy too.}

Ximen Surin's lips drew a very soft curve.

"As what of the disciple is feeling, so too was the teacher. Besides, what teacher would want to see her disciple suffer? Don't even mention such absurd things."

"No. No matter how much Master says, it won't work this time."

However, Qing was also tough in its own way.

Since she was not the usual obedient disciple, the master and the disciple argued for a long time, saying who would do what.

Ximen Surin was a little surprised.

\textit{It is annoying that my disciple, who's usually obedient, is rebelling like this, but I am also touched because I know what she's thinking.}

But experiences triumphed.

"It's also for for the sake of your daughter. Is the child my disiple, or you are? If I see my disciple losing her Innate Qi and getting sick, I'll end up resenting the child. Do you really want your daughter to bear that burden?"

"Oh."

It was an extremely lethal method.

\textit{I should have just asked Monk Wunue or Elder Nan-Gong Daero.}

"Uh, um. I'll think about it a little more. Now that I think about it, it might be a little early, right?"

"It's not too early. The younger the better. Even at this very moment, her muscles and bones are still stiff and her turbid energy is clinging to her."

"Even if Ciyu's young, she have to prepare herself mentally."

"Disciple, don't be so stubborn and just bring the child."

But isn't it true that you can't just hand over your love?

Qing, who had been hesitating, immediately ran to Ambassador Wunue.

"Monk Wunue, I would like to ask you about the Depilation-and-Marrow-Cleansing. Is it a very burdensome matter?"

"Well, it's not that bad. Normally, you'd have to reach the Unrestrained Realm before you'd even attempt it. By then, even if you lost some of your inner strength, it wouldn't be a big deal. Even if your longevity was damaged, if you're being that specific, it's also damaged by harsh training or bad lifestyle habits."

Ambassador Wunue smiles broadly.

"Did you say Ciyu? The heart of the Cheonhwa Sword has become filled with the compassion of the Buddha."

"Actually, Master was-"

Qing revealed the situation.

Monk Wunue's opinion was not much different from Ximen Surin's.

"At this point, it doesn't really matter how much internal energy you have. The rapid onset of the Half-Road Movement will cause you to have a headache for several days. While this isn't usually the case, it's best to heed your Master's advice."

It would be more efficient for Profound Realm master to perform the Depilation-and-Marrow-Cleansing.

But was Profound Realms master just a master?

Isn't it the representative who was mentioned alongside the name of the sect, the pride of the sect, and the core power of the sect?

So there was actually no reason to ask the experts of Profound Realm to do the Depilation-and-Marrow-Cleansing.

Even Monk Wunue could tell that it was absolutely not for the sake of the sect.

She then heard a similar answer from Nan-Gong Daero.

"Oh, you said you'd take he in as your adopted daughter, but now you're trying to take care of her so much? Yeah, that's a good idea."

"I heard the aftereffects were quite serious."

"Anyway, when you're at Unrestrained Realm, what's important is perfecting your own sword and achieving it. What's so important about Internal Qi or meridians? I even personally cleanse A-Cai."

\textit{Hmm, now that I think about it, Sword Friend's nickname really is A-Cai. It kind of fits.}

"At the time, I thought my swordmanship was almost complete, and I thought I'd soon reach the Profound Realm, so what's the big deal about the meridian being damaged? Above all, seeing my son, how could a father entrust his family's future to someone else? That's what being a parent was all about. I felt like I had to do something more, and I wanted to do it myself. Seeing how he've been lately, I wish I'd just left it to my uncle. But he've made a good friend, and stopped being one-armed bastard. I'm eternally grateful to you."

"Ah. One-armed."

"You're not one-armed, are you? Hmm. You think you'll be fine when you reaches Profound Realm, right? I think it's a good idea. It's a joy to have children, to be able to do things for them. But things don't always go as planned, so, um, remember that. Don't be too pushy and demanding."

"Ah. Yes."

Qing nodded awkwardly.

\textit{I seriously felt awkward listening to parenting talk like that.}

"Oh, that's right. Sir, could I have just one wooden sword? I was going to make one for Ciyu, but woods are scarce in this area."

"Hmm, good. I've left them out in the next room, so take a few. If you're going to spar with the child, you'll need a wooden sword too."

Nan-Gong-daero readily gave permission.

Would he bedgrudges a mere black ironwood sword towards the person he regarded as his son's benefactor?

Of course, the individual costs are quite hefty, but from the Nan-Gong family's perspective, it's hard to call it an expense.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After many deliberations.

\textit{I've decided that it's okay to cause Master some trouble.}

\textit{Of course, since I'm planning to leave Xinying soon, stop by Kongtong Sect, and then go home, it would be okay to just hold off for a bit and carry out the Depilation-and-Marrow-Cleansing secretly.}

\textit{But as Nan-Gong Daero said, he's glad that he can do it.}

\textit{Before I leave Kunlun, I want to give Master a position similar to that of a grandmother.}