\chapter{The God of Life and Death, the One Who Conquers All Diseases (5)}

It was a dramatic agreement, even though the main party involved, Tai Ping, was left out. 

Naturally, Tai Ping felt wronged.

"Elder! What are you saying? You clearly promised to save my life at least once!"

"Didn't I save you? Losing one wrist isn't too bad, is it?"

Qing raised her hand.

"Ah, Senior. Sorry, but I'm planning to take both wrists. Isn't it the law that if you get caught cheating, you lose your wrists?"

"Was there such a law? But isn't that too harsh? At least let him hold a spoon with his own hand."

"Ah, then I'll cut off one hand and one foot."

"Hmm. Alright. That way, he can still eat and move around on his own. Let's do that."

Another dramatic resolution!

Tai Ping jumped up, fell to the ground, and clung to Oh Jeok-hwan's hem.

"No, Elder! Why are you doing this? Have I disappointed you in any way…?"

"No, why are you so foolish? Even if I fought for my life, I'd probably lose. I can't guarantee a one-on-one fight with the Heavenly Flower Sword, let alone against more than one."

"But—"

"Even if I somehow won and survived the immediate danger, could you really say you'd live? Not only the Five Great Families, but the entire Wulin Alliance would hunt you down."

Tai Ping's face turned pale.

"If I fight, whether I win or lose, you'll die. But these juniors here are trying to save face for this incompetent senior and are willing to spare your life. So, haven't I saved your life?"

"That's…!"

"Haven't you heard the saying to be wary of women, children, and the elderly in Jianghu? When a woman with a sword steps forward, you should've been cautious and acted appropriately. Even without that, seeing your behavior, I thought you'd get stabbed sooner or later. So, you should've tempered your greed. Well, with the gold and silver you've amassed, you can live off your wealth now. With money, even without a hand or foot, how inconvenient can it be?"

\textit{It seemed Oh Jeok-hwan hadn't been fond of Tai Ping. }

\textit{Yet, he stepped forward as a bodyguard to repay the debt of his friend's life, truly living up to his reputation as a man of honor.}

\textit{But, hmm, is this really honor? Or not?}

"If I may give you one piece of advice, don't beg me, beg her."

"Oh, Great Hero, I've committed a grave sin! I'll give you all the medicine I have, and from now on, I'll live with a heart of atonement, yes, I'll take care of the sick for the rest of my life!"

Perhaps Oh Jeok-hwan's advice was persuasive, as Tai Ping immediately bowed his head to Qing.

But, well?

Qing had a clear conviction, a standard firmly set in her heart.

Regret is just regret, never atonement.

Realizing the immediate loss and that past choices were wrong doesn't mean understanding it as a sin.

"That's a given. You'll hand over the prescription, right?"

It would be fun to mess with Tai Ping, but this wasn't about hobbies.

The most important thing was the prescription for the cure.

The medicine's effectiveness was guaranteed by the Tiger-Slaying Swordsman, and with plenty of money for ingredients, knowing how to make it would solve this mess in an instant.

Of course, the wrist and foot would still be taken.

After receiving the prescription and verifying its authenticity.

If cut beforehand, he might harbor resentment and tamper with the prescription.

And seeing his relieved expression after thinking his wrist and foot were safe, only to have them cut later, would be amusing.

But Tai Ping's response?

"That, that's not possible…"

"What? You can't hand over the prescription? Well, being brave is good too. Wrist? Foot? Where should I start cutting? I'll carve it into a pretty star shape—"

"That's not it! That's not it!"

Tai Ping hesitated, glancing around.

As Qing took a step forward, he hastily explained.

"The, the prescription, actually, the Hua Tuo Gongjin Pill isn't my medicine…"

Qing's brow furrowed again.

An ominous feeling.

"Hmm. So you're really a shaman? Why, did Hua Tuo's ghost possess you to make the medicine?"

"No, I just received the medicine as instructed, and in exchange for the medicine's price, I gathered people…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the warehouse, Tai Ping knelt, tightly bound with rope, surrounded by Qing and her group, Lanzhong Daren, and the Tiger-Slaying Swordsman Oh Jeok-hwan.

Somehow, it felt like one more person had joined, but Oh Jeok-hwan had agreed to spare his life, so he needed to see it with his own eyes.

"I originally made a living by alchemy, concocting various tonics and selling them—"

"Speak straight. You're a quack, right? You made fake medicine and sold it, didn't you?"

"That's, it's not fake, if people believe in it and take it, doesn't it become medicine? In that sense, my medicine isn't fake—"

"Sigh."

"Really. Even ordinary spring water, if believed in, can restore vitality as a tonic. In that sense, we did our best."

Using acrobatics to convince people to take the medicine, planting shills to guide public opinion, giving the medicine to prepared patients to induce effects—all to create belief and confidence in the medicine's efficacy…

"Who cares? Your nonsense is too long."

Honestly, it was a bit interesting to listen to, but it couldn't go on forever.

Tai Ping was a wandering quack.

By his own claim, he never concocted harmful medicine.

Others might mix in poppy seeds or poisonous mushrooms to create an immediate, dazed effect, but he strictly used only harmless ingredients.

Of course, the people who heard that thought, this guy probably did make harmful medicine, but anyway.

While wandering, one day someone approached Tai Ping and asked if he wanted to start a big business.

"An important part is missing. Who?"

"I don't know. He called himself Cheon Seo-yu from Beijing, but of course, that's probably made up."

"Wait, you accepted a big business proposal from someone you didn't even know?"

"Hehe, who would try to swindle a poor quack? There's nothing to take from such people."

Quacks were basically poor.

They don't make much money to begin with.

City folks don't fall for quacks, and if they find the acrobatics entertaining, they might buy one as a souvenir, but even then, after giving a big cut to the acrobat, there's nothing left.

Country bumpkins are easily fooled, but they're too poor to make it worthwhile.

So, swindlers don't bother trying to cheat quacks.

Thus, if someone proposes a business to a quack, it's a chance to make a big score by selling your face.

After all, wandering quacks can just sell their face, make a quick buck, and move on.

Qing thought.

\textit{Hmm. Evil Karma numbers really doesn't lie.}

"Hehe, but this Tai Ping would've refused if it were truly evil. But, there's a special medicine for the current epidemic of the Bai people's pox, and I was asked to sell it."

They needed many slaves, so in exchange for the medicine's price, they'd take people and pay handsomely, promising more medicine in the future.

It was during this profitable time.

While wandering through cities and villages, they finally reached Kunming.

When Qing stepped forward and offered to buy all the medicine at ten taels each, which was a lot of money, Tai Ping almost screamed in joy.

Inside, he thought he'd hit the jackpot, holding back cheers a hundred times over, managing his expression briefly.

Qing not only wanted to buy all the medicine but also demanded more be made.

Tai Ping only received the cure at a low price and resold it; he didn't have the ability to concoct it himself.

So, what could he do?

Sadly, he had to give up.

But Qing didn't give up.

Moreover, Qing was the type to quickly draw her sword if words didn't work.

So, in the end, it came to this.

"I've told you everything…"

Silence hung in the air.

It wasn't just that the full extent of the scam was revealed.

Something smelled fishy.

It smelled like a conspiracy.

"So, someone has the prescription for the epidemic's cure and is using it as bait to gather people?"

"Yes!"

"Hmm. Good."

"Then…"

Hope flickered in Tai Ping's eyes.

Qing nodded and said.

"Do you prefer water or fire? Or both? Choose as you like."

"What do you mean…?"

"Choose whether to drown or burn. If you choose both, I'll boil you in water."

Tai Ping jumped a foot in the air, even while bound.

His wide-eyed, terrified expression satisfied Qing's heart.

Oh Jeok-hwan stepped forward, shielding Tai Ping.

"Heavenly Flower Sword? This goes against our agreement."

"Ah, Elder…!"

"Senior. Don't you no longer have a reason to defend this swindler? This guy was never a doctor or anything, and you were deceived too, so originally, honor or whatever—"

"No, that's not it. Whether this guy is a doctor or a swindler, whether he made the medicine or got it from somewhere, isn't important. My friend was saved by the medicine he provided, so I'm repaying the debt with my life."

"Elder…!"

Tai Ping saw Mount Tai in Oh Jeok-hwan's back, who was standing guard in front of him.

But it was only for a moment.

"So, as promised, cut off one wrist and one foot and end it at that. I'll ask this of you."

"Elder…?"

"Hmm. Then, what if we meet later? Can I kill him then?"

"Well, I can't take responsibility for a lifetime."

"Then, if I let him go and immediately catch him?"

"That's a bit much, isn't it? You should at least give him time to leave before saying you spared him."

"One day?"

"Give him three days. He'll only have one foot, after all."

"Alright. Three days. Hey, you heard that?"

"Spare me, please…!"

As Tai Ping bowed his head while bound, Qing casually dropped a remark.

"Well, it's up to you. First, where did you sell the people? If you have the slave documents, you won't just disappear, right? There must be someone who takes them somewhere."

\textit{They were people who sold themselves for their parents, children, or siblings.}

\textit{Of course, since Tai Ping's tricks were confirmed, there was no coercion or threats—just pure personal choices.}

\textit{Foolish choices, too.}

\textit{Even if the patient recovered, could they be happy knowing their family sold themselves for their life?}

\textit{But those who chose to sacrifice themselves to save their family shouldn't suffer.}

\textit{Because, well, do we even need a reason?}

\textit{There's one real master and three amateurs here, right?}

\textit{Not just that.}

\textit{With the prescription, we can defeat the epidemic.}

\textit{And while we're at it, slicing up such a vile scoundrel, pulling out his guts, and drenching in blood—yes, it's been a while.}

\textit{I had a run in the Forbidden City, but eh, that doesn't count.}

What Qing wants isn't a life-or-death fight against a strong opponent or a duel with a worthy rival.

'Ah, I want to tear apart weak villains! I want to slowly torture and taunt those weaker than me!'

It's Qing's simple wish, repeated dozens of times a day.

\textit{But now, with this intense premonition, how can I resist?}
