\chapter{The God of Life and Death, the One Who Conquers All Diseases (2)}

Suddenly, the number of patients surged, and so did the workload.

Where would the new patients be placed, and where would their families stay?

The critically ill were gathered in the Jangyun Sect's estate, while the less severe patients were accommodated in nearby houses.

But this meant that the original residents had to move, and since the quarantine zone's housing wasn't spacious, multiple families had to be assigned to live together……

"With all this work, should I really leaving?"

"…Stay and help for a few more days."

Lanzhong Daren, who had earlier insisted on her leaving, now seemed overwhelmed by the sudden influx of tasks.

It was understandable. Expanding the patient quarters and reorganizing the living arrangements for the quarantined families was no small feat. Even if they didn't voice it, the residents would naturally feel discontent.

Moving from their original homes was already a hassle, and if the new accommodations were smaller, older, or farther from Lanzhong Daren's residence, it would only add to their frustration.

The atmosphere between the original residents and the newcomers wasn't great either. The original residents felt that their established order was being disrupted by the newcomers, while the newcomers, having been driven from their homes, were already in a bad mood and didn't appreciate the cold stares.

Thus, it was better for a martial artist with a sword at their waist to handle this.

After all, swords were scary.

To the common folk, martial artists are just as fearsome and dangerous as officials.

So, between moving patients, relocating original residents, and finding new places for the quarantined families, the day passed in a blur of activity.

As the sun set and the day's work came to an end—

"Elder, you might want to come out."

"What now?"

"It seems the relief supplies have arrived."

The relief grain had arrived.

Lanzhong Daren was dumbfounded.

The workings of officials were said to be as slow as the changing of seasons.

When an official handles a matter, it's like the seasons turning, taking an eternity with no sign of resolution.

He had heard that Qing had persuaded them to promise relief grain, but he hadn't really expected it.

In fact, he was more worried.

Qing had a fiery temper and was somewhat extreme, and as a martial artist, she might have threatened the official in a fit of anger.

Officials were known to be narrow-minded, with no room for even a drop of tears, so even if she had threatened him, it would only have worked in the moment.

Once she turned her back, he would surely change his expression and harbor resentment.

But now?

In just half a day?

And at night?

Unlike Qing's homeland, in Zhongyuan—and indeed, in this era—no matter how urgent, night was not a time for work.

Because it's dark.

And yet, the notoriously slow government had sent relief grain in the middle of the night, torches and all?

What kind of miracle was this?

Moreover.

"Ahem. Elder, you've worked so hard. We're truly grateful for all your efforts."

"Prefect? You came out at this hour?"

"Ha ha ha. Ahem, well, the cries of the people were too loud, so I couldn't just sit still."

Lanzhong Daren seriously wondered if the Prefect had eaten something wrong.

Of course, he was a relatively well-regarded official, not overly corrupt and known for upholding the law, even considered somewhat of a model official.

But this was the same man who had firmly stated that while he could quarantine the sick, he couldn't provide support. And yet, here he was, personally leading a cart of relief grain.

As Lanzhong Daren blinked in confusion, the Prefect subtly glanced at the woman standing beside him.

'Prefect, it seems we need to provide some relief grain to the quarantine zone……'

'What are you talking about? Why relief grain? There's no reason to give it to patients who've already been dealt with. It's a waste.'

'Well, Elder Lanzhong is taking care of the patients here.'

'Tsk, if we just let them die, the plague will go away. But with his reputation, we can't just drive him out.'

'Umm, the Inspector is helping Elder Lanzhong—'

'Kyaaak!!!'

The Inspector, it seemed, was a formidable woman with a high-ranking belt.

Indeed, she was formidable.

Since the Inspector hadn't revealed her identity, it was awkward to act like he knew.

But he couldn't just leave the situation unexplained.

So the Prefect awkwardly began to explain.

"Well, ahem. According to the law, relief grain is lent to the people in times of natural disasters like floods, droughts, or locust plagues, right?"

That's right. Relief grain wasn't free.

When a natural disaster ruins a year's harvest, it's lent at a low interest rate.

So releasing relief grain to patients who might not recover is risky, as there's no guarantee it will be repaid.

It could end up being a waste of the nation's resources.

"Well, I'll write you a promissory note. Let's see, about two taels of gold—"

"No, no, no, ahem. How could I, as the Prefect responsible for the city's affairs, ignore the people's suffering? This time, I'll cover it with my own funds……"

"Eh, don't be modest. Take it. And I doubt it'll actually come from your own pocket?"

"Ha ha ha."

The Prefect was sweating profusely.

Even if he dipped into his personal funds, he'd surely find a way to replenish them. And the way officials replenish their funds is through the 'sincerity' of their subordinates.

And where does that 'sincerity' come from?

So even if the Prefect used his personal funds, it would ultimately be the people of Kunming who'd end up paying for it.

With that, the Prefect's cold sweat began to flow even more intensely.

"Ah. I'm not blaming you, Prefect. I've heard you're deeply respected. You can't let personal feelings interfere with state affairs."

"That's, that's right."

"But you were a bit harsh, weren't you?"

"I'll correct that……"

The Prefect was oscillating between heaven and hell.

After all, as the leader of a province, there weren't many people above him, and those few could wipe out entire families with just a few words.

They held the power of life and death.

And the Inspector was even more terrifying.

Even if some higher-up wanted to take down the Prefect, a high-ranking official like him could mobilize all his connections, factions, and alliances to defend himself.

But the Inspector could directly send a message to the Emperor saying, 'I don't like that guy, let's just kill him'.

However, Qing had no intention of wielding her power.

From what she could see, the Prefect wasn't particularly evil.

For a high-ranking official in Zhongyuan, his level of evil was below that of a beast, barely qualifying as human.

At this level, he could be considered a model official, a paragon of virtue.

There was no reason to torment a capable person with petty crimes.

Though she had been given the position of Inspector, Qing didn't really want to use it.

The taste of power is sweet, but if she indulged in it, she'd become Inspector Ximen Tianhua, not martial artist Ximen Qing.

Of course, that didn't mean she had to be overly frugal, but still.

But the Prefect had to be careful.

Though her face was covered, his instincts honed from years in the bureaucracy told him that the mysterious Inspector didn't seem to harbor any hostility, which was a great relief.

"Ahem, well, Elder Lanzhong, if you have any requests, please let me know. You've worked hard for the people, and I'll do my best to help."

This wasn't a genuine offer to help, but just a polite farewell, like when people in Qing's homeland say, 'Let's have a meal sometime', as a way of saying goodbye.

But suddenly, Qing's eyes lit up.

If the Prefect dipped into his personal funds, so what?

It all came from the city's people anyway.

In a situation where fellow citizens are suffering, everyone should pitch in and help.

"My, you truly are a model of a compassionate official. Then, without further ado, we'll need about twenty bolts of clean cotton cloth. We've been tearing up good clothes to use as bandages. To restore the patients' vitality, they'll need some meat, so while you're at it, send some meat—any kind will do, even the tough cuts. Oh, and plenty of salt. Ah, Elder, is there anything else you need?"

Lanzhong Daren's eyes also lit up.

He had been soliciting donations from the wealthy, and now, with this atmosphere, he had truly struck gold!

"There's more than one or two things we need. If I had known the Prefect is so generous, I would have asked for more help earlier. Do you have a brush? Wait, I'll write it down for you."

"No, you're even making a list, ahem."

And so, the Prefect of Kunming was thoroughly fleeced.

The somewhat pitiful sight of him retreating wasn't just a trick of the eyes.

As Lanzhong Daren watched his retreating figure with a satisfied expression, he suddenly asked,

"Fairy, when you become a Great Master, do even high-ranking officials like the Prefect tremble before you?"

The Prefect wasn't trembling because Qing was a great master.

But?

After a moment of thought, Qing replied,

"Probably? Everyone values their life, after all."

"……."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Thanks to the Kunming Prefect's astonishing generosity, the quarantine zone's living conditions had improved to the point where no one went hungry.

The relief grain was old, and the other supplies they had requested (or rather, extorted) were of low quality, but quantity over quality.

Still, it was better than the days of barely edible gruel made from whatever grains and scraps they could find.

Compared to those times, it was like night and day, a complete transformation.

But what truly pleased Lanzhong Daren was something else.

Since the Fairy and her friends had arrived, the people's expressions had brightened.

Why?

Because young, attractive men and women were walking around.

The Fairy, with her stunningly beautiful face—so beautiful it was a problem—hid her face, but her friends were also quite good-looking.

There was a muscular guy, and another who covered his face, but even just the lower half of his face suggested he was no ordinary handsome man.

With such people walking around, the quarantined residents began to look more like humans and less like beggars.

Originally, the quarantined residents had looked like beggars.

They were hungry, and being confined made it difficult to maintain their appearance.

When life becomes too hard, people stop caring for themselves, stop washing, stop working, and become as shabby as beggars.

Their hair was disheveled, their clothes wrinkled and dirty. While common folk weren't known for being particularly clean, the quarantined residents had stopped even pretending to wash.

It was hard to tell if they were quarantined patients and their families or just a group of beggars.

But now, one by one, they began to comb their hair neatly, smooth out their clothes, and their previously vacant eyes began to show signs of life.

Now, even in the midst of quarantine, you could occasionally see couples shyly holding hands and walking around.

While diagnosis, prescriptions, and medicine are important, the patient's will to live is equally crucial.

How much guilt must the patients have felt, seeing their families, who were also confined and on the brink of starvation, looking like beggars?

But now, with no fear of starvation and their families looking healthier, the patients' spirits were lifted, which would greatly help them overcome their illness.

So now.

"You've done enough. Go now."

"Eh, Elder. You keep trying to send me away. It's hurtful."

"I'm telling you to go because you're no longer needed. Don't you see the atmosphere in the village? There's no quarantine zone as bright as this. The rest is just a matter of refining the prescriptions based on what we've learned."

"Wouldn't it be faster to complete the prescriptions with Tang Lan-Ah here?"

"Now that things have improved, I'll visit Kunming's medical halls and recruit some physicians. There'll be some who'll be intrigued by the challenge of creating a prescription for an unknown disease. If it were still a beggar's den, they'd have run away, but now that they see the non-patients walking around decently, they'll feel reassured that it's not the plague."

The same words can carry different nuances depending on the speaker's tone.

Before, it was clear he was trying to force her out.

But now, there was a sense of satisfaction and pride in how well she had done.

So, from Qing's perspective, it seemed she could leave the rest to him.

"Are you sure it's okay to go?"

"Well, the only trouble now is those pesky medicine peddlers sneaking in. But with the Prefect's support, I can just have the soldiers at the quarantine gate drive them away."

"Eh? Medicine peddlers?"

"Yes, those scoundrels of the world. Before you came, a couple of them showed up and caused quite a mess."

The easiest people to deceive are the desperate.

And patients are the desperate.

So there are those who prey on patients with scams, and they're the wandering medicine peddlers.

"Ah, those quacks."

Qing immediately understood.

Because in her homeland, 'medicine peddlers' referred to fraudsters selling fake medicine.

Medicine should be handled by pharmacists, and treatment by doctors.

But these peddlers, who aren't pharmacists, sell medicine, and it's unlikely they're selling the real thing.

At that moment.

"Elder? You might want to come out."

In Zhongyuan, there's a saying that if you talk about Cao Cao, he'll appear. In Qing's homeland, they say if you talk about a tiger, it will come.

This is a long-proven law of the world.

"What's this about life and death? A divine being? Some grand physician has arrived and says he has a good medicine, so he's asking us to gather the people."