\chapter{The God of Life and Death, the One Who Conquers All Diseases (4)}

"It's clear that you're helping Lanzhong Daren, but if I hand over the medicine to you, wouldn't you just dissect it and try to replicate it? If you start mass-producing someone else's medicine, what doctor in the world would bother creating their own prescriptions?"

He was implying that if she bought the medicine, she'd just make counterfeit versions. 

Of course, she'd might analyze a few to figure out the active ingredients, but replicating the medicine? That was absurd.

"Wait, what? Medicine isn't like tasting food and instantly knowing the ingredients. What kind of nonsense is that?"

Even the recipes of famous chefs are hard to reverse-engineer just by looking at the final product.

Cooking involves ingredients that retain their texture, taste, and aroma, yet it's still difficult to replicate. 

If that's the case with cooking, how much harder would it be with medicine?

Medicine, after all, often doesn't retain the original form of its ingredients. 

Most medicinal materials are processed before use—some are dried and ground, others burned to ash, some juiced and solidified, and others boiled down to a concentrated liquid.

Pills are just compressed powder, and decoctions are strained through fine cloth, leaving only the liquid.

"Ahem, even if there's a slight chance, you can't just steal someone else's hard work. Tsk, these people have no sense of business ethics."

\textit{Business ethics? }

\textit{Why was a doctor talking about business ethics?}

Of course, doctors sell their skills to make money, so in a way, they're merchants.

But doctors also hold power.

They've mastered the difficult art of manipulating life and death, so even if they're dirty and petty, desperate people will cling to them.

"Whatever. Just prescribe the medicine. You said you'd stay for about five days, right? Then you can personally confirm that the patients take it. Lanzhong Daren won't interfere. Elder, is that okay? Yes, let's save lives first. I'll pay for each person when you leave. Deal?"

"W-Wait, no payment later! What if they take the medicine and then pretend they don't know anything?"

"What do you take people for? Fine, I'll give each patient ten taels, and you can collect it directly when they take the medicine."

"No, that won't work either! I'm not selling!"

The vein on Qing's forehead twitched uncontrollably. She clenched and unclenched her fists without realizing it.

"What's this? Why won't you sell even when I'm offering money?"

"Ahem. Well, originally, you see, it's like this! Don't you know the saying that life and death are in the hands of heaven? Birth, aging, sickness, and death are all determined by heaven. If someone dies from illness, it's heaven's will. If they live, that's also heaven's will!"

"What kind of doctor talks like that? So, you're saying that a doctor saving lives is going against heaven's will? That's heresy!"

"Exactly! That's why, to save a life, you must show enough sincerity to avoid heaven's wrath! If someone's illness is cured by gold thrown at them by others, do you think heaven would allow such luck? Heaven would be angry and deliver an even more gruesome death!"

Silence fell over the crowd. 

'What kind of nonsense was this?'

Qing tried to summarize.

"So, you're saying that illness is fate, and a doctor curing it is heresy?"

"Yes!"

"And if someone else pays for the cure, the patient will just get sick again, so they must show their own sincerity?"

"Exactly!"

"So, stop with the nonsense and just sell your body already?"

"Right!"

Tai Ping shouted confidently, then froze.

"Ahem, selling one's body? No, it's about showing sincerity to cure the patient. Haven't you heard of the story of Mai Shen Zhang Fu? A man sold himself into slavery to bury his father, and heaven was moved by his filial piety. It's the same principle."

He really seemed to love the story of 賣身葬父.

Mai Shen Zhang Fu. Selling oneself to bury one's father.

About 1,500 years ago, there was a poor but filial man named Dong Yong.

When his father died, he was too poor to afford a funeral.

Dong Yong went to a wealthy man in the village and offered to work as a slave in exchange for the money to bury his father. The dead man received a lavish funeral, and the living man became a miserable slave.

In the midst of this miserable life, a stunningly beautiful woman suddenly appeared before Dong Yong, relentlessly proposing marriage. 

Overwhelmed by her persistence, Dong Yong eventually agreed.

But this woman was incredibly skilled!

She started raising silkworms and soon produced silk in abundance.

It was a miracle—silk seemed to multiply endlessly.

Within a month, she sold enough silk to pay off Dong Yong's debt, and he was finally free. Then, the woman declared:

'I am actually the daughter of the Jade Emperor. I was moved by your filial piety and came to help you. Now that you're free, live well.'

With that, she flew away, leaving Dong Yong staring up at the sky in shock.

The moral of the story? If you want to win a beautiful woman, sell yourself first. Heaven will be moved and grant your wish.

Want to move heaven? Sell yourself.

This wasn't just for men. In Qing's homeland, there was the famous story of the filial daughter Sim Cheong, a woman who sold herself to save her father.

Anyway.

By now, Qing had figured it out.

\textit{This scoundrel—his real profession wasn't being a doctor, a shaman, or a merchant. He was a human trafficker.}

\textit{The ten taels of gold is just an excuse. He wanted to get people to sign contracts and sell them into slavery.}

\textit{I don't know much about human trafficking, but ten taels per person seems about right.}

Qing took a deep breath. It took almost superhuman patience to hold back.

\textit{If only his medicine didn't work.}

"Fine. I'll pay twenty taels."

"Didn't you hear me? If someone else pays, it's just corruption."

"Thirty taels."

"Thirty, forty, even a hundred taels—it's no use. Ha, you think money can solve everything? It's about sincerity, sincerity."

Qing's smile widened unnaturally, her lips stretching to her ears.

\textit{You little shit, death penalty for you.}

"Hehehe, you're really refusing wine and choosing vinegar, huh?"

Suddenly, Qing had an epiphany.

\textit{So this is why people say 'refusing wine and choosing vinegar'.}

\textit{It really sticks to your tongue.}

Qing's aura flared up, dark clouds of energy filling the air. Even though her face was covered, her red, round eyes and wide, menacing grin were visible.

"Eek! Elder! Elder!"

Tai Ping screamed, falling back on his butt. He scrambled away, hiding behind the martial artist who had been standing behind him.

The middle-aged martial artist sighed deeply and reluctantly stepped forward.

"…Stop."

Qing rarely stopped when told to, but this time, she did. Because the middle-aged martial artist's faint blue number of Righteous Karma, though almost nonexistent, was still visible.

"Don't take it too hard. I don't particularly like this guy, but I owe him a debt and promised to protect him. He saved the life of a close friend. A wanderer without honor is no better than a bandit. I promised my life in exchange for his, so I must keep my word."

"Senior, this man exploits the weak by holding medicine over them, and now he's trying to sell them into slavery. He's a shameless villain."

"Ahem, his business practices are dirty, but he's not a fraud. The medicine is real. I've seen his patients recover with his prescriptions."

"But—"

"Listen. He's not selling fake goods. Pricing is up to the seller. If you don't like it, don't buy it. Even if the price is outrageous, you can't force him. It's despicable for a doctor to profit so much from prescriptions, but it's not against the law."

The middle-aged martial artist wasn't wrong. 

The issue of medicine pricing and morality—even in Qing's homeland, there were pharmaceutical companies that made even demons cringe.

But legally, there was no problem.

The law doesn't enforce morality.

Or perhaps it's because the money squeezed from people's blood and tears is shared with those who make the laws.

\textit{But what's the law?}

\textit{I'm a martial artist.}

\textit{Martial artists don't follow the law.}

\textit{If anything, it's the crime of being despicable.}

One of the things Qing liked most about Zhongyuan was the environment where private retribution against scoundrels was praised as chivalry, where you can punish the assholes who deserve to be punished.

"Senior, is it right for a patient's family to sell themselves to save their loved one? The one who sells themselves becomes a miserable slave, and the patient, though cured, will be heartbroken knowing their family suffered for them. Both the patient and their family will be in agony."

"Ahem."

"I've clearly offered money, and honestly, even if the common folk sold themselves, who would pay thirty taels? Yet he insists on selling people with such sophistry. This isn't about profit—it's a manifestation of his vile nature. How could he do this without finding joy in the suffering of others?""

"Hmm."

"You spoke of honor, but honor is something kept between people. Such a vile beast doesn't deserve human honor."

"Even if someone is a villain who deserves to die, if they've done you a favor, you must repay it. If you judge others and act according to your own interests, how can you call that honor? My honor is like that, so don't take it too hard and step back."

The middle-aged man said this as he drew his sword.

The faint red light surrounding the blade, though weak, was enough to make one's heart skip a beat—it was the aura of a master swordsman.

\textit{Wait, what? }

\textit{Now even a quack's bodyguard is using Sword Force?}

At that moment.

"Wait, I'm Zhuge Lixian from the Zhuge family. Senior, may I ask who you are?"

"Zhuge Lixian, the Beastly Sage? Ahem, I'm Oh Jeok-hwan."

Qing hesitated for a moment.

\textit{Three, two, one.}

\textit{Hmm, if he's using Sword Force, he must be famous.}

"Oh Jeok-hwan!" "The Tiger-Slaying Swordsman!" "The Tiger-Slaying Swordsman!"

Qing breathed a sigh of relief at the voices of her friends echoing in her ears.

\textit{Good, he's a famous person.}

Qing tilted her head slightly. As if on cue, Zhuge Lixian whispered in her ear.

"Sister, he's the Tiger-Slaying Swordsman, Oh Jeok-hwan. He's said to be at Harmony Realm…"

The Tiger-Slaying Swordsman, Oh Jeok-hwan.

During his travels, Oh Jeok-hwan was treated kindly by a couple in a village. The next day, they received news that their son had been killed by a tiger.

To repay their kindness, Oh Jeok-hwan vowed to avenge their son. He tracked the tiger for a year and finally killed it, earning his title.

So, the Tiger-Slaying Swordsman—the swordsman who slew the tiger.

\textit{Listening to this, it was clear he was a man of honor, worthy of his reputation.}

\textit{Even if it's just a single point, I think I know why he have accumulated Righteous Karma.}

Qing clasped her fists in salute.

"Senior Tiger-Slaying Swordsman, I, Ximen Qing of the Divine Maiden Sect, pay my respects."

"Ah. The Heavenly Flower Sword, was it?"

Oh Jeok-hwan looked troubled.

\textit{The Heavenly Flower Sword? Rumor had it she was the brightest star of Wulin, a member of the myterious Divine Maiden Sect, a disciple of the Zenith Among Women, the youngest ever to reach the Transcendent Realm.}

"Peng Daesan."

"…Tang Lan-Ah."

The introductions continued, becoming even more bewildering.

\textit{Why are the heirs of the Five Great Families all gathered here in this remote place? Friendships are usually formed among equals, and the Five Great Families would naturally stick together, but why here?}

\textit{Still, honor is honor.}

\textit{Even if it's for a villain who deserves death, if you owe them a debt, you must repay it.}

\textit{It's not some grand principle. A martial artist without honor is no better than a bandit—or worse, a murderer.}

\textit{I don't want to make my entire life up until now just the life of a thief and murderer.}

So, Oh Jeok-hwan steeled his resolve.

\textit{As I have done so far, since Tai Ping saved my friend's life, I should repay him by saving his life as well.}

Thus, Oh Jeok-hwan spoke.

"…Even if he's a scoundrel, spare his life. If you agree to that, I won't stop you."

"Ah, so beating him until he spills the prescription and cutting his wrists to prevent him from causing more trouble is okay?"

Oh Jeok-hwan nodded. 

After all, he had repaid the debt by sparing Tai Ping's life. He had done his part.
