\chapter{The God of Life and Death, the One Who Conquers All Diseases (3)}

In the open space, two large flags fluttered in the wind, their golden characters written on red cloth catching the eye.

萬病征服醫仙. The Immortal Doctor Who Conquers All Illnesses.

生死換歡神醫. The Divine Doctor Who Exchanges Life and Death for Happiness.

In front of these flags stood a man, his hands clasped behind his back, observing the crowd that had gathered. His appearance was striking, to say the least. His robe, made of multicolored fabric, fluttered in the wind, making him look more like a shaman than a doctor.

Qing's impression was simple.

\textit{Hmm. A quack.}

Moreover, judging by the aura of malevolence surrounding him, he was the worst kind of fraud.

But it was too early to judge.

One couldn't judge a person solely by their appearance, and a high level Evil Karma didn't necessarily mean he was a swindler.

After all, while all swindlers might had high Evil Karma, not everyone with high Evil Karma was a swindler.

Fortunately, Qing had a useful human encyclopedia by her side, though he was quite noisy.

"Zhuge, have you heard of him?"

"A quack. Never heard of him in my life."

It was none other than Zhuge Lixian, the walking encyclopedia. Qing decided to cross-check.

"Lan-Ah, have you heard of him?"

"He's a quack. What kind of doctor writes their name like that? If he fails to cure someone, he'll get stabbed to death."

It was a taboo for doctors.

A doctor could only prescribe what they knew, but life and death ultimately depended on the patient.

However, if a patient died after treatment, people's fickle hearts would inevitably blame the doctor.

Especially if he claimed to cure everything, the resentment would skyrocket if he failed. How could he handle that?

From the start, his shaman-like attire didn't look like a doctor's at all. To put it bluntly, he wasn't acting like a "doctor."

However, the martial artist quietly placing his hand on the hilt of his sword behind the quack was no fraud. The sharp aura he exuded was enough to silence the crowd gathered in the open space.

No matter how you looked at it, the quack's appearance was suspicious, but with a martial artist (presumably a master) backing him up, it somehow seemed credible.

Martial artists valued their reputation, so no matter how much gold was offered, they wouldn't stoop to being a mere enforcer for a swindler.

"Elder, what should we do?"

"Let's hear what he has to say first. There's always a chance, however slim, that he might have a genuine prescription."

"His appearance suggests otherwise."

"Once, there was a guy who accidentally created a genuine prescription and sold it. Like a cow catching a mouse with its hind leg. Only one, though."

Lanzhong Daren was clearly displeased but remained cautious. If the prescription worked, what did appearance matter?

The quack, glancing around the crowd, flinched slightly when he saw Qing's group. Suspicious, but given the martial artists in fine clothes mixed among the patients, it was understandable.

"Hmm. Is everyone here? Well, I'm here to give you a chance to recover, but if you're not interested, it's your loss."

The quack snapped his fingers, and a servant holding a flag stepped forward and announced:

"This is the Immortal Doctor Who Conquers All Illnesses! The Divine Doctor Who Exchanges Life and Death for Joy! The true successor of Hua Tuo, the master of all diseases and the savior of those destined to die — Master Taiping!"

"Master Taiping was originally a divine child from Zhengzhou, who received Hua Tuo's divine teachings and inherited his medical skills! Thus, he is the true successor of Hua Tuo!"

Qing's group collectively furrowed their brows. The more they listened, the more absurd it sounded.

He wasn't just dressed like a shaman—he was a shaman. And he was invoking Hua Tuo.

According to the servants, he had received divine teachings from Hua Tuo, the legendary doctor, and had directly inherited his medical skills.

\textit{Who would believe such nonsense?}

\textit{What kind of shaman is that? Where even you could find a legit shaman?}

That was the impression of the Earthwork Fairy, known for her spiritual powers in Guangxi Province.

But here, the crowd of onlookers—family and friends of the patients—seemed deeply impressed.

"Wow." "Hua Tuo!" "It's Hua Tuo's disciple!"

In an era where even basic education was a luxury, such colorful packaging worked well on the ignorant common folk. Especially for the families of the patients.

The families of the patients were desperate. If someone claimed they could cure their loved ones, they were ready to believe anything.

They wanted to believe, clinging to any straw of hope.

But.

A little thought revealed how absurd it was.

If he had learned medicine directly from Hua Tuo, so what?

Hua Tuo lived roughly 1,500 years ago. Learning medicine from a doctor 1,500 years ago would mean using 1,500-year-old medical knowledge. Medicine had advanced since then, and many prescriptions from that era were outright dangerous.

Even if Hua Tuo came back to life, he wouldn't even qualify as a medical apprentice today. Medicine had progressed too much in 1,500 years.

But then?

"I am Chailha from Yeokmun! Master Taiping solved the plague of Yeokmun with his miraculous prescription! I was so moved that I decided to serve him!"

"I am Yeo Seung-sam from Sinpyeong! Master Taiping also subdued the plague of Sinpyeong!"

Sinpyeong, Wongang—wherever these places were, they claimed he had already proven his effectiveness. The servants weren't just servants; they were patients he had cured who had chosen to follow him.

"Elder? Do you know these places? They say he's already proven himself there."

"It's a common swindler's trick. We can't verify it immediately, so how can we know if it's true? Well, it would be nice if it were."

At that moment:

"I am Yu Dong from Wongang! Everyone, this man is truly a divine doctor! In Wongang, the vicious Bai Pox spread, and everyone was in despair. But then, this man—"

"What nonsense is this? Bai Pox?"

Lanzhong Daren exploded in anger. The crowd's attention turned to him.

"Bai Pox? Who dares to name a disease like that?"

"I named it. Isn't it the doctor who creates the prescription who names the disease? I've already created a prescription for Bai Pox, so I have the right to name it."

Taiping calmly replied. The crowd's attention shifted back to him.

"You scoundrel! How dare you name a disease like that!"

"Why not? The Bai barbarians spread it, and it causes mucosal ulcers and blisters, so it's a pox. Isn't it logical to call it the Bai Pox?"

Qing unconsciously nodded.

\textit{Hmm. So it's the Bai people's pox, right?}

\textit{Why, back then, that pneumonia was rampant, um, come to think of it, it was endless. It was my neighborhood…}

Back in her homeland, there was a severe plague that swept the world, and its origin was none other than Wuhan, Hubei Province.

Now, to Qing, it was also her hometown because the Divine Maiden Sect was in Hubei.

"You scoundrel! Whether Bai or Han, who in this world hasn't mixed blood? We've been living together for 500 years! If you trace their genealogy, there's no one in Yunnan who doesn't have Bai blood mixed with them! If what you say is true, the plague should have started in Zhongyuan, not Yunnan!"

"Well, ahem, we'll figure that out later……"

"How dare you, as a doctor, name a disease based on unverified facts!"

Qing nodded again.

Indeed, in this era, pure-blooded ethnic groups were nonexistent. 

Especially after the previous dynasty's brutal policies, mixing bloodlines like livestock, there were no pure-blooded ethnic groups left in the world.

And especially the Han people, who prided themselves as the core of Zhongyuan—not a single pure-blooded Han remained. It was an open secret.

\textit{Moreover, was there a disease that only affected a specific ethnic group? Hmm. Smallpox? That wasn't about ethnicity but more about regions, like a sterile room being contaminated. Anyway.}

\textit{A disease that only affects a specific ethnic group? Thinking about it, it's nonsense.}

As the cold gazes turned toward him, Taiping shamelessly changed his tune.

"Anyway, what does the disease's name matter? The important thing is that I've discovered a prescription for this terrible disease. This is the Hua Tuo Gongjin Pill. Not only will it cure the disease, but it will also restore the patient's vitality, making them healthier than before and granting them a long, illness-free life. This is the legacy of Hua Tuo!"

"The legacy of Hua Tuo?"

"Why, don't you believe me? But you will. Take one pill morning, noon, and night, and in three days, the patient will rise from their bed. To prove it, I'll stay here until the patient recovers. Then you'll believe me."

Lanzhong Daren visibly panicked. Stay until the patient recovers?

Swindlers usually sold their medicine and fled immediately. If the medicine they sold had no effect, it was a blessing. Often, the side effects killed people.

But he claimed to cure the patient in three days and would stay until it was confirmed? That was confidence only possible if the prescription was genuine.

The crowd buzzed with excitement. They were relieved, saying they were saved, that heaven had helped.

But it was short-lived.

"However, the medicine uses rare ingredients, so it's not cheap. But how can I profit from saving lives? So I'll only charge the cost of the ingredients—ten taels of gold."

Ten taels of gold?

Most people in Zhongyuan rarely even held gold.

Of course, as in a famous novel from Qing's homeland, if one saved diligently, it wasn't impossible.

But there was no reason to save for years just to hold a high-denomination note.

But ten taels of gold for medicine? How many patients could afford that?

"Of course! I know it's a hefty sum. But I still have mountains of patients to treat, and to continue making the medicine, I need to cover the cost. I can't save you and leave others to die. But! There's a way!"

The crowd turned their attention to Taiping.

"Fortunately, some generous patrons have offered to help. They'll give you a chance to work off the debt. Three years for men, two years for women, and just one year for young women."

He was asking them to sell their bodies. Especially the short term for young women—his ulterior motives were glaringly obvious.

"In the Book of Filial Piety, it says that if you lack money for your parents' funeral, you should sell your body to fulfill your filial duty. If that's the case for funerals, what about saving your sick parents? And for parents with sick children, even without my saying, you'd naturally want to save your children."

He was saying they should sell their bodies for their parents.

"Let me reiterate, there's no need to worry about the medicine's effectiveness. I'll stay here for about five days, so you can confirm your family's recovery before leaving with me."

At this point, it seemed the medicine might actually work. But the price was so exorbitant that he was practically forcing them to sell their bodies. What a scoundrel.

\textit{Hmm. No wonder his Evil Karma is so high.}

\textit{But at least he's selling genuine medicine. Better than a swindler.}

\textit{And the high price?}

Qing stepped forward.

"I'll cover the cost for everyone! Everyone! I'll pay for the medicine!"

Silence fell over the open space.

They had seen the Fairy caring for the patients, so they knew her. But her saying she'd pay for everyone's medicine—wasn't she saying she'd buy it and distribute it?

Suddenly, the people couldn't look up, their eyes downcast.

'The Elder always called her 'Fairy', but she truly is so radiant, it brings tears to my eyes……'

But Taiping's pupils trembled. He was clearly panicked.

"All of them? That would be a thousand taels of gold."

"Only a hundred doses? No, I'll pay for the ingredients, so you can make more. Right?"

"Well, yes! But I don't accept promissory notes. A thousand taels of gold, in cash!"

"Then I'll exchange it for you. Yi-mei, can you go to the market? Yes, a thousand taels. No, make it two thousand taels. Ah, but is that okay? Two thousand taels of gold would be hard to carry around, right?"

"Well, ahem, that……"

Taiping stammered suspiciously. Then, he smirked slyly.

"No. I can't sell it to you."

Qing's brow furrowed deeply.

\textit{What's this scoundrel up to now?}
