\chapter{The God of Life and Death, the One Who Conquers All Diseases (1)}

"Last night was rough. Fairy, you've done enough, so go now. The Jangyun Sect's mischief has been dealt with, more or less. I called you to handle that, not because I'm short on hands."

Inside the quarantine zone, Lanzhong Daren wasn't overwhelmingly busy.

When the plague broke out, the Kunming branch had sealed off the northern part of the city and gathered all the sick and their families in one place.

This meant that, apart from the patients, there were also many able-bodied workers who had been brought in.

Lanzhong Daren was only treating the critically ill, while the less severe cases were being cared for by others.

From the beginning, Lanzhong Daren had been going around the city collecting money, which indicated that his workload wasn't excessive.

However, the past couple of days were different.

About forty Jangyun Sect disciples had suddenly fallen seriously ill, forcing Lanzhong Daren to stay up all night caring for the patients.

If it weren't for Qing and Tang Lan-Ah, who had forced him to rest, he would have truly spent the entire night tending to the sick.

"Eh? You were checking pulses late into the night yesterday. It's a busy time now, so I should lend a hand. Where would I go?"

"Enough. I don't need to borrow the hands of a half-trained physician. The severe cases are somewhat under control, and the rest just need occasional checks."

"Eh. Tang Lan-Ah is here too. I've only read a few medical books, but Tang Lan-Ah is a proper physician."

"Tsk, you talk too much. Just go if I tell you to."

"No, Elder, why are you acting like this? Suddenly telling me to leave. Is something wrong?"

Lanzhong Daren clicks his tongue in dissatisfaction.

"What's wrong? You, a woman with a child, how can you be so careless? Didn't you see the Jangyun Sect disciples fall ill? The number of people who got sick overnight is overwhelming. You might be fine as a master, but the child needs to be carefully looked after."

He's telling her to leave because Ciyu could get infected.

Qing smiles and retorts.

"Eh, you said it wouldn't spread."

"That was until yesterday. If a strong man like that could get so severely ill, it's a different story."

"Maybe they all ate something bad. And Ciyu is always running around with the kids. If it were contagious, they would have fallen ill first."

Children are the type to quickly become friends, laughing like dolphins when they see each other.

Ciyu has been busy playing with all the kids in the quarantine zone, only returning when the sun sets and it gets dark.

Since the kids in the quarantine zone are fine, how could Ciyu possibly get sick?

Ciyu's level, to put it simply, is somewhere in the second tier.

She's taken elixirs and undergone rigorous training, and she's even practiced the Yijin Cleansing Method, a Qi Cultivation Divine Art.

Though she doesn't know how to control her Inner Qi, her body is already in a state where Qi flows smoothly.

When Qi flows smoothly, vitality rises, and when vitality rises, the body becomes strong and resistant to illness, which is why martial artists rarely fall ill.

"No, it's not like you'll be taking care of them forever. Why get attached to the patients? Just leave."

"Why are you so desperate to send me away? And if I'm not going to take care of them forever, does that mean I can't help at all?"

"Why aren't you listening to what the elder is saying? Anyway, you're too kind for your own good."

Breaking news: Lanzhong Daren claimed Qing is 'too kind'.

A statement that would make countless people speechless, clutching their chests in disbelief.

"Hehe."

"That's not a compliment. It's an insult. A person needs to know when to be ruthless and when to be kind. You're too naive, thinking being kind is always good. It just means you're easy to take advantage of, kid."

"Eh, Elder, how can you say that? There are countless people who respect Lanzhong Daren. After all, you've spent your life caring for the poor."

It was just the usual back-and-forth banter, each praising the other.

But suddenly, Lanzhong Daren's expression hardened, and a shadow fell over his wrinkled face.

"…Just go."

"Elder?"

"Don't say such terrifying things. I'm just a wretched quack who's lived too long."

"Elder? Are you okay?"

"Go. Please. Just because the plague hasn't spread so far doesn't mean it won't in the future. This crazy old man, in his senility, dragged in a woman with a child. I'm the mad one, truly mad. Leave quickly. That's the best way to help this old man. I'm so worried I can't even check pulses properly, so stop lingering around and go."

When Lanzhong Daren goes this far, it's awkward to insist on staying to help.

So what can she do? Pack up and leave.

"Ah, um. Elder, I'll write you more promissory notes. But will the local pharmacies accept Taeqing Trading Company promissory notes? I'll check with the pharmacy and get you something that can be cashed immediately. I'll send it to you later."

"Good. That's thoughtful. And when you're done, don't linger. Return to Zhongyuan. It's best to avoid areas where disease is spreading."

Though it's not something someone who always goes to disease-ridden areas should say.

Anyway, just as Qing awkwardly gets up to leave—

"Elder! Elder, it's an emergency!"

A voice urgently calls for Lanzhong Daren.

Then, a frantic announcement comes from beyond the door.

"Outside, a large group of patients is gathering!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At the temporary quarantine gate, the unloading of patients is in full swing.

Unloading, as in setting down the cargo.

And it's an accurate description.

They're carefully placing the patients, packed into carts, onto the ground as if stacking corpses.

This is just for the critically ill who can't move. On the other side, less severe patients are staggering in, dragging their feet.

The quarantine zone isn't just for the sick.

The soldiers standing guard with spears are keeping their distance, fearing infection, while those unloading the patients are the families who will also be quarantined.

There are already over forty critically ill patients lying on the ground, and when you add their families, the number of newly quarantined people is staggering.

And that's just the critically ill. If you include the less severe patients and their families, the number easily exceeds two hundred.

Lanzhong Daren strides through the crowd and approaches a man.

Wearing an official's hat, he seems to be the person in charge of the quarantine operation, or someone of similar authority.

"Hey, what's going on? Where did all these patients come from?"

"Ah, Elder. A large group of patients came from the market district. It's chaos. The branch leader ordered them all to be rounded up and quarantined. Who knows where the plague is spreading now? Do you have any prescriptions?"

"Hey, you. Just dumping them here like this won't help. If hundreds of people suddenly arrive, where will they stay? How will you feed them? If you're going to gather people, you need to release grain rations too, so we can save those on the brink and treat them."

"Ah, Elder, I'm just following orders. What can I do?"

"What kind of nonsense is that? Are you saying you're going to gather them here and let them starve to death?"

"Ahem. Honestly, this isn't something I should be telling you, Elder, but we didn't ask you to take care of the patients. I don't have the authority to do anything about it."

"What, what!?"

Lanzhong Daren's jaw dropped.

What kind of talk is this from an official?

The government didn't ask Lanzhong Daren to take care of the patients; he's doing it on his own, so he has no right to interfere in government affairs.

But for someone in charge to actually say such things, it's no wonder Lanzhong Daren was speechless.

However.

Qing was far from speechless.

"Do you think everything that comes out of your mouth is worth saying? And if you know it's not something to tell the Elder, why are you spouting nonsense?"

"Ahem. It's just a figure of speech."

"Speak properly. If the Elder is taking care of the plague, prescriptions will come eventually. So what are you saying? That you didn't ask for it?"

As Qing fires back, the man lowers his head.

At least he seems to feel some shame.

"Fairy, don't be too harsh. This guy has dipped into his own pockets to help. Those below have no power; they just follow orders."

"That's right…"

"Who's giving such terrible orders? If it weren't for the Elder, these patients would have starved to death long ago. Are you just gathering them here to let them die?"

The official then spilled out an excuse.

"Well, the branch leader said we should save those who can be saved."

"So you're going to let the living patients die? The Elder is here, and if you just release the relief grain—wait, where's the relief grain? Isn't relief grain supposed to be stored for times like this? If you don't release it now, when will you? So you're just leaving them to die?"

"The relief grain is for natural disasters or locust plagues. We can't just release it for patients who might not recover……"

In other words, since there's no guarantee the patients will recover even with the relief grain, they won't give it.

So, they're just gathering them here to let them die if they can't hold on.

"What, what kind of nonsense is this?"

"Kunming has tens of thousands of households. It's difficult to release relief grain for patients with no guarantee of recovery……"

The official continues to defend the branch leader.

In fact, by Zhongyuan standards, the branch leader's decision is rather merciful.

In such a large city, when a plague breaks out, it's common to bury the sick alive.

At least they're gathering them in one place and giving them a chance to survive.

In an era where access to medicine is limited, the sick are already half-dead.

So there's no reason to go out of the way to save them by releasing relief grain.

The best way to stop the plague is for all the patients to disappeared, whether through death or recovery.

If you just let them die, the plague would end.

But if you kept them alive with relief grain, you were just prolonging the source of the plague……

After hearing this, Qing understood the branch leader's decision.

This wasn't a world like Qing's homeland, where you keep people alive and eventually develop a cure.

It was a cold decision, but it was about saving tens of thousands in the city by sacrificing a few patients.

"But, Young Lady, who are you to say such things……."

"Hmm, why don't we step aside for a moment?"

Qing pulled the official aside and slip him a silk pouch.

"Ahem, it's a bit light……. I'll pass it on to the Prefect\footnote{知府大人; Zhifu Daren}, but even so, we can't just release relief grain. If a flood hits during the next harvest, we'll have used the relief grain to save the sick, and the healthy will starve."

"That's not gold, you know? Take a look inside."

"Ah, it's not a gift. What is it—gasp."

The official opens it and sees a shiny Inspector's badge greeting him with a 'Hi! I'm the Inspector'.

His face immediately paled, and he straightened his posture.

"Shh. Go tell the Prefect. All the people of the world are the Emperor's property, so no subordinate can decide to take or discard them, even if they're old or sick. Therefore, release the relief grain immediately to feed them."

"Y-yes, ma'am!"

Qing could understands the Prefect's decision.

If it were someone else's business, she would have just sighed and said, 'That's how it is in this primitive, ancient Zhongyuan.'

But with the Elder putting in so much effort, how could she just let it go?

In this ruthless era, she couldn't let the noble efforts of a good person go to waste, and it shouldn't be allowed.

If bad people are punished, shouldn't good people be rewarded?

As the official scurried away, Qing returns to Lanzhong Daren with a sly smile.

"Elder, you don't have to worry about the grain. They're going to send relief grain."

"What, how?"

"Hmm, I persuaded them."

"Hey, that guy doesn't have the authority. Did you threaten to kill him if he didn't comply?"

"Eyy, I said I persuaded them."

Lanzhong Daren's expression brightened.

The issue of where to house the patients and their families is still there, but the biggest problem was the grain, wasn't it?

Since that's resolved, the method doesn't matter.
