\chapter{It Seems You're Upset (1)}

Several figures were lurking over the Five Poisons Sect's headquarters, or rather, the ruins that were once the Five Poisons Sect's headquarters, which was swept away by the shells and burned by the flames. 

The Five Poisons Sect was a poisonous den.

Thus, it was possible that there were still functioning traps or toxins left, and although the ground was scorched, one could not know what lurked beneath it.

Therefore, capable masters with the ability to handle such dangers had embarked on an internal search.

"Hmm. It's here too."

Ji Yun Zhenren was tapping the ground with his sword.

A subtle flow of Qi brushed under Qing's feet.

Ji Yun Zhenren was not merely prodding the debris; he was spreading his Qi in all directions like a droplet on the surface of a lake.

\textit{It seemed like a kind of detection method, but what exactly is he doing?}

\textit{It was an amazing skill that no matter how much I watched and pondered, I couldn't figure it out.}

\textit{Just how far does Hyun-kyung's ability go!}

That indeed would be something no one would know aside from Hyun-gyeong…

The remarkable technique of the Ji Yun Zhenren did not end there.

Once recognizing the underground space, wouldn't Ji Yun Zhenren pierced the entrance in a way only a true master could?

And that too with just a single finger.

Ji Yun Zhenren merely pointed with a finger, yet the fingertip of the supreme martial artist possessed destructive power that could break through the closed underground entrance.

"Guys. Here too."

Immediately, the masters of the Diancang Sect rushed over, thrusting the heads of their shovels into the ground and starting to dig through the debris.

That was truly astonishing.

Considering the danger, those below the level of Hwa-gyeong were prohibited from entering, and all the Taoists of the Diancang Sect involved in the search were martial artists of Hwa-gyeong.

Where in the world could you see masters of Hwa-gyeong digging the ground?

If they were of Hwa-gyeong caliber, even shoveling would be immensely powerful.

Dirt and ash flew up as they worked, swiftly revealing a square vertical shaft.

"Let's see. I don't sense any sign of life."

Ji Yun Zhenren leapt down first.

One might question if he knew what was down there before jumping down, but considering that he was a master of Hyun-gyeong, what could he possibly fear?

In fact, this was already a repeated process several times.

In the primordial ancient Zhongyuan, basements would surely be cool spaces fit for storages.

Ji Yun Zhenren tapped the ground, the masters dug to reveal the underground space entrance, and the the Flashing sword led the charge.

The other disciples stood guard outside.

While this may seem like a natural process, it was indeed the most definitive difference between Orthodox sects and Unorthodox groups.

For those of the Unorthodox sects, there was no reason for those in high positions to lead in inherently dangerous places.

In the first place, a master would not descend into such disorder.

– Hmm? Heavenly Blossom Sword, come down here.

From the hole in the ground, Ji Yun Zhenren's calm voice floated up.

Upon jumping down, she was hit with the damp, musty air specific to underground spaces, along with a sharp, heavy smell of blood that pierced her insides.

Qing took a deep breath.

\textit{Hmm, it seems a bit fragrant?}

"Ugh, I gues he was unlucky."

It was a small room with debris from one person shot in one direction.

The room was surrounded by bookshelves.

One side was half-collapsed, but the opposite side maintained the shape of an intact library, only splattered with blood and flesh.

Perhaps a blind shell had rolled in from above, and just happened to be blocked by the figure standing in front of it.

Thanks to this, half of the books were preserved intact; calling it bad luck for the perpetrator would indeed make more sense.

"It looks like a library. But why underground?"

Ji Yun Zhenren mumbled in puzzlement.

The underground was inherently humid and stuffy, making it a poor place for storing books.

Qing's eyes sparkled as she ran her fingertips along the bookshelves.

This was the nasty habit of a martial arts thief, as merely touching a complete Secret Manual was enough for immediate acquisition.

However, unfortunately, there was nothing of sort.

\textit{What are they, if they're not Secret Manuals?}

\textit{If they're not Secret Manuals, why hide it underground? Or are they fake Secret Manuals? A trap perhaps?}

Qing pulled out a book and glanced down at it.

In the dim light, it was not an ideal environment to read, but Qing's physique had transcended humanity, and her night vision was even sharper than that of nocturnal beasts, so there were no problems.

Flipping open a title-less book for a quick glance, only incoherent information was lined up.

\begin{quote}
	……A mixture of poisonous flower and nectar. Half a qian\footnote{錢; Ancient Chinese unit of weight. 1 qian = 3.69 grams}.

A 27-year-old man, sturdy physique weighing 140 kilograms.

After one shichen's passage, blood spots appeared; complaints of pain began from the tips of fingers.

After two shichen's passage…
\end{quote}

Qing possessed skills recognized to be on par with that of a medical practitioner, but even without that, understanding this text would not be difficult at all.

Qing picked out another book to scan through.

Then another book, and yet another.

A deep wrinkle formed on Qing's forehead.

\textit{Crazy bastards; these are records of human experimentation.}

Some books recorded poisoning by gender, age, and body type, while others detailed blood slowly drawn away, along with the recorded time of death. Some even had detailed illustrations of a heart, annotated with the original owner's characteristics.

Such books lay all around.

A sinister hue flickered in Qing's eyes.

\textit{These Blood Cult bastards—}

In that moment.

Clap! An unexpectedly cheerful clapping sound brought Qing back to her senses.

"Don't hate them too much. The deeds of Blood Cult were always like this. Therefore, there's no need for you to hate them. These scum are not worth being angry toward. They really should be skinned and tossed in saltwater."

"Huh?"

For someone to say 'don't hate', it sure seemed like a voice filled with anger.

\textit{What is this?}

\textit{You're saying not to hate.}

\textit{Am I supposed to do it?}

Qing blinked, bewildered.

At the sinister hue that concealed itself, Ji Yun Zhenren smiled like a true Daoist.

"One kills fleas and crushes mosquitoes, yet doesn't hate those insects. They were merely harmful things to be eradicated."

"Ist there anyone who doesn't hates mosquitoes?"

"There was once a person who was tormented by mosquitoes; the hatred seeped deep into their bones. That person lived next to a reed field, so it was only natural for the mosquitoes to be rampant."

Reeds grow in flooded lands, so it would be expected for them to be swarmed with mosquitoes.

"So, didn't he give up farming one day and start living only to catch mosquitoes?"

However, even if one person diligently catches mosquitoes, they won't disappear.

Because of the reed field.

Even if one tried to catch mosquitoes in their breeding ground, no matter how many they catch, there will always be more.

"So, he thought to himself that in order to completely exterminate these mosquitoes, he must set the reeds on fire and burn them all away. He did it, and the fire spread across the reeds, resulting in him being burned to death too."

Ji Yun Zhenren took on a solemn expression.

"It's possible to harbor hate. But if one continues to keep hatred in their heart, at some point, it will overflow, becoming resentment. And when that hatred grows heavier than oneself, one ends up living not for themselves but for that hatred. Just like he abandoned farming."

And in the end, he ended up burning to death, attempting to kill mosquitoes but managing to kill himself in the process.

"You have a natural disposition to kill, so you must not waste your hatred on these matters. You could burn the mosquitoes, tear off their wings, dunk them in water, or play with them to vent your anger, but your entire life ought not to be spent chasing mosquitoes."

Qing tilted her head.

That's when the Master of Fortune spoke again.

"I always tell the disciples of the Diancang Sect. Hatred and gambling. Gambling was indeed like that. If one enjoys gambling for fun, they should not feel wronged even if they lose. Because whether you drink or have tea, it's only natural to spend gold and silver when you have fun. So if one enjoyed gambling, it's merely paying the price."

Gambling means betting.

When one played properly, one spent money, and even if they lose that money through gambling, thinking of it as paying for the fun was acceptable.

"But if one desires not to enjoy gambling but to make money from it, problems arise. A person can become mad in an instant. People who become obsessed with gambling will often sell their family members to prepare money for betting, so saying not to treat a gambling addict like a person isn't just a saying."

"Hmm."

It's exactly the sort of thing a Taoist would say.

So it sounded profound and seemed to hold deep meaning, but upon careful reflection, it felt subtle and ambiguous.

"So what should we do with these? Should we send them to the Divine Maiden Sect?"

"Huh. These?"

"Then? Should we burn all of them? Of course, they are dreadful books, but at a glance, they seem quite useful. If it were up to me, I would want to throw them to our sect's clinic, but since the Diancang Sect hasn't done anything, it wouldn't feel right. Grabbing their tail was your doing, and firing the cannon was your skill. All the Diancang Sect did was rush in to watch."

"Uh, um."

"I understand your reluctance, but discarding books that are already written would just be a waste in the end. It may not be something a Taoist should say, but what can be done about what has already occurred? Using what was left could perhaps do good for those unfortunate souls as well. Well, anyway."

"Then I think we should send them to the Alliance first. If any sect wants them, they can take copies for study, or would sending them to the Tang Family first be better? It's their expertise, right? The Alliance is too far; so I will have them write some copies first."

"Hmm. While this is also material about the poison used by the Blood Cult, it still pertains to the human body, so digging into it would provide exceptional value. It doesn't necessarily related to poisons. It's not something you can easily entrust to someone else, is it? To begin with, no one is as knowledgeable about medicine and poisons as the Tang Family, so wouldn't the Tang Family get the majority of the gains?"

"Eh, well, still, I'm sure they will share the important parts, but they should take care of their side income. Just getting the prescriptions used by the Blood Cult would be worthwhile. After all, um, no."

From the outset, Divine Maiden Sect was not that large of a sect, to the extent that it wasn't usually considered a separate sect.

It's not for nothing that they diligently had their pulse checked every time Tang Lan-Ah comes to visit.

So even if the Divine Maiden Sect took the books, there wouldn't particularly be anyone to study it, and it would be better to receive materials made by experts.

What's the point of hiding the books so tightly?

"But we are still one family in the Orthodox Wulin, so it would be nice if we could all see it and someone could gain something from it."

At that, Zi Yun Zhenren smiled gently.

If a disciple of Diancang Sect spoke such naive words, it would be infuriating, however, it would equally fill him with much delight.

\textit{Isn't this the great Dao that puts the collective good above personal interest?}

Ji Yun Zhenren made up his mind once again.

\textit{Indeed, I must find the Earthly Killing Star and make them my disciple…!}

It was the moment when the Elder Slayer skill struck another nail into his heart and sounded the clarion call of victory.