\chapter{It Seems You're Upset (2)}

The path north of Jinping north lead back to Kunming.

The quarantine area for the sick Qing returned to semed somehow mellow, or rather, more peaceful.

Children were playing, and adults were sitting on benches, basking in the warm winter sunlight reminiscent of a spring day in Kunming, living like carefree individuals.

Originally, the atmosphere was that the sick lay groaning while their families wore tired expressions due to caring for them, although children still played. However, this time it was different.

What could this possibly mean?

It meant that the illness was being held at bay.

While the symptoms had improved, the quarantine remained, so everyone seemed to be enjoying their time leisurely without anything to do.

Upon entering a certain unidentifiable faction's quarantine area where they were making a ruckus, an elderly man immediately caught their attention.

The elder, Langzhong Daren, looked at Qing and said one sentence.

"So you're here?"

It was a rather straightforward welcome.

Even though not just Qing but a group of martial artists rushed in all at once.

"Elder, this is Langzhong Daren. Langzhong Daren, this is Ji Yun Zhenren from the Diancang Sect."

"It's been a while, Elder."

"You should have come a bit earlier. You weren't busy when it mattered. I'm using the help of the outsiders in the matter of Yunnan."

"Things will be busy going forward, so please bear with me."

It seemed they were old friens.

While the grumbling Langzhong Daren was having a sweet smile exchange with Ji Yun Zhenren, a noise sounded from the door, and a shrill voice pierced Qing's ears.

"Ah! Qing'er dear!"

Then, with a whoosh, Tang Lan-Ah leaped out like a cicada clinging to an old tree and hugged her.

It seemed like some kind of violent welcome, but Qing thought nothing about it.

\textit{Well, seeing Ciyu being hugged all the time, Tang Lan-Ah must have wanted to try it too.}

"Are you not hurt? Did you get a hole pierced or a shard stuck in you or any tendons damaged or cut?"

"I'm fine, you know? Nothing happened?"

"A lot happened. Every day without Qing'er was a lot for me."

"Ah, I almost felt excited. So, what about the prescriptions? Is it completed now? The patients look well!"

"Not yet. I'm mixing various prescriptions to neutralize the poison. The medicine was potent, so I think I'll need to observe a bit longer."

The symptoms was indeed intertwined with toxicity alongside the illness, so while there was a lot of improvement, a complete prescription was yet to be finalized.

However, as observed in the peaceful atmosphere of the quarantine area, it seemed that the prescriptions were nearly complete.

At that moment.

Another hand that held Qing was there.

Xue Iri was a hugging her quite tightly, causing the round face of the girl Lan-Ahh, wedged between them, to be squished.

"What now? Are you not going away?"

"It's me. Yes."

What's this? It's me. Not going away? Not going.

Only when playing tricks does she sneakily use honorifics, perhaps because Guhyung was a bit, or rather, quite trivial; one might say she isn't foolish but rather petty.

"What about San… Never mind."

Qing shook her head, who was about to ask about the well-being of Peng Daesan.

Women around who seemed not to be working were moving back and forth, casting their eyes towards a specific direction, so she knew exactly where he was.

In any case, it was time for the reunion of the Half-Sword Double-Saber Society!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Dali County.

More precisely, it's called Dali Prefecture.

As it was the capital of the Dali Kingdom, which has become affiliated with Zhongyuan, it's rightfully called 府 (Fu) rather than 縣 (Xian).

However, it has been called Dali for a long time, so they don't strictly separate the two terms anymore.

The most famous thing about Dali was, undeniably, its rocks.

The marble of Dali.

Dali marble was indeed that marble!

Thus, Dali\footnote{大理; Great Texture (marble)}!

Nevertheless, they just passed through Dali.

What also made Dali famous was the massive lake that resembles an ear, called Erhai Lake.

As indicated by the name implying a sea\footnote{The 海 (Hai) in 洱海 (Erhai) means 'ocean'}, this was truly a gigantic lake that corresponds closely to about fifty-five Yeouido according to the most easily understood measurement unit of Qing's ethnicity.

And across the lake, there lay a great natural barrier draped in eternal snow, extending left and right, and this mountain range was known as Changshan.

Furthermore, Changshan was also known as Diancangshan.

Thus, Diancang!

The martial artists of the Diancang Sect left some behind to guard the quarantine area, and Qing and company finally arrived at their intended destination, the Diancang Sect.

When visiting another's sect, the first thing to do was to greet the elder.

The Sect Leader of the Diancang Sect, Ji Gan Zhenren, had thick white hair, resembling an immortal in demeanor, which was indeed quite rare.

Unlike in the past, the current Wulin is characterized by the tacit adherence with Wulin Alliance, with the elders rising and retiring quickly, forming a roughly similar age group.

Considering that the Sect Leader of the Divine Maiden Sect, Heavenly Silent Sword Wang-Juhi, bore a very warm, amiable appearance of a neighborhood auntie, the aged appearance of the Diancang Sect's Sect Leader indeed stood out as strange.

"Ha ha, you've had quite a hard time."

"No, Ji Yun Zhenren was also there."

"That's what I mean by you've had a hard time…"

At that, Ji Gan Zhenren let out a deep sigh.

"That Senior speaks thoughtlessly, no, has spoken far too thoughtlessly, no, he has no thought at all. The person itself isn't evil. If there's anything held in your heart, just think of it as meeting an eccentric senior. That guy, or rather, that Senior, probably spoke without much thought and has likely forgotten what he said. It wasn't driven by malice, so you needn't feel burdened…"(the rest is omitted)

Qing realized.

\textit{Ah. That's why you've aged so much…}

\textit{Thoughts about the mess that his Senior might cause had clearly worried him.}

"I really don't mind; you don't have to worry. Also, I tend to speak rather bluntly myself, so I actually enjoyed it."

"How can you speak so beautifully? Even speaking like this is quite appreciated. So you wish to see the Absolute Sword Wall? Hah, that bastard Ji Yun, abandoned all the disciples and came back alone."

Having taken the elite of the main Diancang swordsmen with him, Gilun had gone around here and there while leaving detachments.

It wasn't just the quarantine area at Kunming, but due to public sentiment against Bai people due to thrumor of Bai Pox rumors and other issues, they were dispatched in pairs to various cities and eventually, the only one who returned was Ji Yun Zhenren himself.

"Oh, how long will we be staying? Until the Diancang disciples return?"

"No. Those kids probably won't figure anything out simply by looking. Wathing others shooting arrows won't improve one's own archery, they're too underdeveloped to learn just from seeing others. It would be better to ask the masters for advice and share insights instead. The Grand Elders are a bunch of careless idlers; they should contribute to the sect like this."

\textit{They say that if you are next to ink, the black will spread to you. Isn't Sect Leader's speech quite extreme?}

After greeting the Sect Leader and returning to the guest room, familiar faces came out to greet her.

Among them, a particularly tired-looking kid widened her big eyes even wider and stared at Qing.

Then, with childlike impudence, she jumped into her arms effortlessly.

Of course, Qing's embrace was soft and springy enough to provide enough cushioning for the child to avoid injury.

Qing twirled around with Ciyu in her arms.

There was a high-pitched laughter that went "keeheehee"—no, what kind of dolphin is that? But, that's usually how a child laughs.

"How have you been, Ciyu?"

"Ung. Ung."

"Yi-mei, everything's fine, right?"

"Ung. Ung."

\textit{Children tend to quickly adopt speech patterns, so it seems Ciyu had quickly picked up Yi-mei's habit of responding 'Yes' twice.}

\textit{By the way, seeing Heema, heh, I guess we should share a bed together as family today.}

With a sly glint in her eye, Qing inadvertently looked at Jian Buxi, but their eyes didn't quite meet, and it felt somewhat downcast.

"By the way. I received a message from the trading company."

"Huh? From the trading company? Xue Family Trading Company? How—, I guess they sent someone to the Diancang Sect."

"Yeah. It seems like they found something?"

"What is it?"

"Weren't Xiao-mei asked them to find them before we left?"

"Me? Ah."

Suddenly, something flickered in Qing's mind.

\textit{Thinking about it, I asked Xue Ganom to find out about the master of the Ten Great Demonic Arts.}

"Oh, did they find it? Hmm, but they could have just sent it to let me know back, why send someone all the way here? Is it nearby?"

"Umm."

Jian Buxi's 'Umm' meant no.

\textit{What kind of phrase does a grown woman like her possess? Could it be that she just pretending to be cute? But Yi-mei is the epitome of seductress, or maybe closer to obscenity, but well, I kinda like it.}

"They said it's Mount Changbai?"

"Mount Changbai?"

Creases formed on Qing's forehead.

Mount Changbai was considered a sacred mountain by the Qing's (true) ethnic group, called Baekdusan by the people of her homeland.

The problem was that Mount Changbai was located at the far east and northeast of Zhongyuan.

\textit{I would have to stop by the Divine Maiden Sect anyway, so why are they send someone all the way to Diancang Sect…}

\textit{Not to mention, given the nature of the news, it would only make sense that the messenger from the trading company had to come in person…}

Of course, rationally speaking, that's how it should be.

But religious sentiments were inherently nrrational; religion belongs to the realm of emotions, so how could Qing grasp the zeal of the believers determined to convey answers to their supreme deity?

She was unaware that, as they exchanged this news, a bloody incident had sprung up.

"The rumor there was that a monster with blackened blood vessels erupted from the entire body. So, they call it… the Changbai Monster."

At that, Qing suddenly felt an unknown chill.

\textit{Somehow, it seems like a very dangerous monster\footnote{천지 괴물; Lake Cheonji Monster} wouldn't do, right?? Hmm? Why, what? Why not? What? No? Can't? Rat?}

"—Han, they call it."

"Phew, what is this? Why do I feel relieved? It's as if I almost faced great trouble? Why?"

No one would know that.

"Anyway, it's a monster from Mount Changbai, right?"

"Yeah. They say it's a monster with blackened blood vessels that tears beasts apart raw."

"Oh, that thing."

That was the characteristic of the Reverse Blood Demon, as explained by Xue Ga-nom, the greatest intellectual of the Central Plains.

\textit{Reverse Blood Demon is the one who mastered Pa-cheon Yeokhyeol Demonic Art, right? No, wasn't it a really long and complex name? What was it again?}

The answer was indeed the Pa-cheon Yeokhyeol Susim-ja Cheomgyeol.

Naturally, it would be expected that anyone would be confused about it, and it would be more astonishing to find someone who could memorize it correctly, so Qing couldn't be blamed for her ignorance this time.

Scratching her head, Qing thought.

\textit{But Mount Changbai…isn't that quite far?}

\textit{In any case, to go to the Liaodong Peninsula, I'll have to pass through Jianping.}

\textit{Might as well stop by that cave where I first awakened. Back then, I was so flustered and busy adapting to the primordial ancient Zhongyuan, so perhaps there was something left behind?}

\textit{If I think about it that way, it's a bit far, but it can't be helped.}

\textit{Wait, isn't it still a bit too far…?}