\chapter{It Seems You're Upset (3)}

The next day.

The path to the Absolute Sword Wall of the Diancang Sect could be described as, well, it feels suddenly like an atmosphere of a picnic or perhaps more like a mountain outing? Not quite so.

"Yesterday, I went to the reservoir in front and caught a catfish that must have been at least a hundred years old. Honestly, without joking, it must be quite the spiritual beast."

"Oh, shall we have a catfish soup then? Lately, my bones have been aching, and I think a good bowl of that would make me feel better."

"Hmph, such a spiritual beast, how could I harm it? Since I've felt the thrill of fishing, I let it go. That guy must have been quite scared after the ordeal."

"Here he goes again. What's up with him bragging about catching a big one? Nobody has actually seen the big catch he's talking about."

"Ah, don't say that. Fishing is a skill too. I have become proficient in it and reached such a state that even the spirits guarding the water currents are easily caught by me."

"Do you know what they say, as people age, they get bolder? Last time I went with him, he couldn't catch even one small fish, and now he thinks he has become a master?"

"That's because Senior Brother has no luck in fishing. What kind of bad luck it was to be around someone who has no luck in fishing at all."

Hmm. Yes, this atmosphere.

Qing thought of an appropriate description.

It feels as if a group of seniors from a seniors' center was going on an outing together…

Indeed, the observers from the Diancang Sect were all elders with white hair, the Great Elders.

If they could gain insights from observing Qing's demonstration, it was more likely to be from seasoned masters equipped with both skill and experience.

So, it would be better for the Grand Elders who are willing to give their wisdom to the sect to come and observe, rather than for the incompetent disciples to observe.

That was the judgment of the Sect Leader of the Diancang Sect.

As they were leisurely ascending the mountain path.

Suddenly, unusual trees caught their eyes.

They were young trees that weren't very tall, but the peculiar thing was that their circumference suddenly decreased around the waist, resembling a thin tree stuck into a thick trunk.

\textit{What is this? How can trees grow like that?}\footnote{They can't, but chalk it up to the mysterious cosmic energy.}

And, among them, there stood an old man leaning at a slight angle.

This was the Heavenly Martial Emperor.

"Ah. Elder. When did you come out?"

"Whenever I want. Do I need to ask permission from a green baby to come out?"

There were always people who say things like this.

As Qing scratched her cheek, she suddenly realized, "Oh."

It meant that whether it was the Grand Emperor Wutian or the Grand Emperor Wuqing, that shockingly unexpected entrance suggested she had already seen traces of the Nine Solitary Sword.

So, could this place be?

\textit{Now that I think about it, the tree itself wasn't like that but rather sprouted from a tree that had been cut once and then regrew again.}

\textit{With such trees filling the area, they were uniformly cut and then sprouted again at one set height, as if measured by a ruler.}

Qing looked around.

The only visible surroundings were those trees that had been cut once and then sprouted again.

In the distance, completely grown trees rose like castle walls, and it was indeed a magnificent scene of a single sword cutting down a vast forest.

"Oh, you weren't carving it into the cliffs of the Diancang Sect. The Movement is probably a horizontal cut, then?"

"Can't you tell? If you have eyes, you should realize.  You act like you figured it out on your own, tsk tsk"

"Hmm, why am I feeling you're extra prickly today?"

"Your heart is prickly. I'm just a manifestation you've created with your image of Heavenly Martial Emperor. Tsk tsk,  it's because you're unsure of your growth."

The Grand Emperor Wutian brought up the idea of the Grand Emperor Wuqing.

The claim was that hew was not the Grand Emperor Wutian himself, but a modified copy of the Grand Emperor Wutian, created by Qing after seeing the sword marks.

Qing narrowed her eyes.

"Is that right? It seems unlikely."

"Or else? Would the long-living Heavenly Martial Emperor stealthily appear? Or did he descend casually from the heavenly realms?"

"Whoa, was he Immortal?"

At that, the Heavenly Martial Emperor chuckled.

"Hah. Where in the world were there any Immortals?"

"Huh? How could there be no Immortals? Isn't this a world where people gather energy, shoot star light, and fly around wielding swords? Seems unlikely there aren't any Immortals."

From Qing's perspective, the cosmic mysteries of Qi, the omnipotent element enabling all nonsense, could not be grasped.

Qi existed, and it emits Sword Qi and Force Compression.

\textit{Not only that?}

\textit{I too have been learning martial arts through brain-injection style education, and my master flies around wielding swords, Yun Yuanying creating the undead, and and those monks of the Cheonnyeo Temple from Tianzu even bring the souls of the other world to the primitive ancient Zhongyuan through some ritual.}

\textit{Isn't it ludicrous to say there were no Immortals here?}

But the standards were always those of Qing.

The eyebrows of the Great Master MuQing lowered.

He looked at Qing as if seeing an utterly foolish person and clicked his tongue.

"Is that the same? The circulation of Qi in nature is as natural as breathing. The story of Immortals was what you humans constructed. What has Qi got to do with that?"

To the Zhongyuan people, Immortals were akin to the European unicorns in Qing's homeland.

There were creatures with long necks and long noses in the world, and some even regenerate into two creatures if halved.

So how could you confidently say that horned horses don't exist?

That logic was absurd and incomprehensible, yet what can be done about things that don't exist?

To the Zhongyuan people, Immortals were those kinds of beings.

But Qing wasn't a Zhongyuan person.

And above all, it seems quite suspicious.

\textit{Is he really the Grand Emperor Wuqing? Not the Grand Emperor Wutian himself?}

"Hmmm."

"Enough. It's the Fourth Movement, Severing Ties, Cutting Love."

The first three Movements had already been confirmed.

For the Diancang Sect, it was unfortunate news.

斷緣切愛.

斷緣 (Duan Yuan) or severance of ties refers to a term used in Buddhism indicating that one cuts ties with their Karma.

Here, the ties being cut refer to worldly connections, which could also mean a departure from secular life.

Moreover, it signifies the mind of a practitioner, often associated with cutting off afflictions or attachments.

切愛 (Qie Ai) or cutting love was also a similar term.

It too was a term from Buddhism, denoting greed and attachment, which were indeed the causes of reincarnation, aiming for nirvana by cutting them off, which also a mindset of a Daoist.

"To be honest, the Diancang lot isn't even worthy of being called Daoists. They barely meet the threshold. Are they really Daoists or merely servants of the Dali royal family?"

The Diancang Sect, being the most secular of the Taoist sects, once acted as the main Taoist temple of the Dali Kingdom, firmly maintaining the roots of the Bai ethnicity.

Of course, that didn't mean that the Diancang Sect discriminates against or refuses other ethnic groups.

However, the cities and villages around Mount Diancang were all cities of Bai ethnic group that originally belonged to the Dali Kingdom, meaning that almost all the disciples were inevitably Bai people as well.

Even when other ethnicities like the Han or Miao clans entered the Diancang Sect, they tended to see themselves as honorary Bai afterward.

"Back in the days of the Dali Kingdom, the Diancang Sect was about half attached to the Dali military, so it was unavoidable. But it’s not like they can maintain that kind of relationship forever, is it?"

"Hmm. I don’t think there’s any particular problem, is there?"

"Why wouldn't there be? The Dali royal family has been utilizing the Diancang Sect almost like their military, and even while focusing on training, they still end up going down the mountain to wander daily. Isn't that how it continues now?"

\textit{Hmm, so there's a story behind the Diancang Sect like that.}

\textit{After all, I have heard that they were currently relatively idle, so the disciples who have come because of the Bai Pox incident are wandering all over Yunnan.}

\textit{Such movements seem justifiable under the notion of protecting the innocent, given the rumors of an outbreak.}

\textit{But can't it be that this is a legitimate activity for a proper sect?}

"And you, of all people, are in that position."

"Huh? Me?"

"Being young—no, being younger—has its contradictions. You've already reached Hwa-gyeong at such a young age, do you think your skills have reached a level where you are unbothered? Do you think you have plenty of time to slowly train and that someday you will certainly reach Hyun-gyeong? What a waste of precious time!"

At that, Qing felt agitated.

"Why do you say such things? I'm being desperate in my own way!"

"Hmph. Desperate, huh? When I was your age, I built a cottage in the mountains and trained all day, practicing breathing for three shichen cycles, then rising to wield my sword again."

Breathing exercises can substitute some sleep but never truly replace it.

In other words, it meant he devoted himself to training without any sleep.

\textit{If someone else said that, I would just nod and feign belief.}

\textit{But somehow, I feel like Heavenly Martial Emperor really did that.}

"So, it's a disconnection of fate when there should be focus. Even for me to perfect a single martial art, human time is too short. Why waste time obsessing over useless relationships and fussing when you should be training the hardest?"

"No, I'm not wasting time."

"Then isn't it a waste? No matter how close of a friend you have, do you expect them to train on your behalf you? Again, let me reiterate, no matter how long you live, at most, you'll only scrape by with a little over a hundred years of life to reach the late stages of Hyun-gyeong."

"Wait, a little over a hundred years means—"

"Ah, look at this talk."

Feeling frustrated, the Great Master MuQing let out a deep sigh.

"Easy there; it's only a little over a hundred years. That's all there is! It's been a thousand years since Master Damo\footnote{Bodhidharma, a Chinese monk from 5th century CE} came from Tianzu, taking in the good of martial arts and spreading it throughout Zhongyuan…"

It took three hundred years for the first martial artist of Harmony Realm to emerge, being Wang Chongyang of the Quanzhen Sect.

The sect established independently by Wang Chongyang's direct disciple was Huashan Sect, the sect established by Wang Chongyang's descendant was Wudang Sect, the sect established by those who remained after the disbandment of Quanzhen Sect was the Zhongnan Sect.

The first Harmony Realm martial artist essentially laid the foundation for three of the Nine Great Sects.

Another four hundred years would then pass before the very first Demonic Ascent appeared, which was the Heavenly Demon, his power alone capable of standing against Zhongyuan.

Fortunately, while facing that, the first martial artist of Profound Realm was born within the Orthodox Sect, barely able to halt Heavenly Demon Cult's world conquest.

"Thus, it took a full seven hundred years for martial arts to be passed down and rise to Profound Realm. Seven hundred years! And only upon reaching Profound Realm one realize that the end of martial arts still feels so far away and indistinct. Yet, a person's life was capped at a little over a hundred and fifty years—merely that!"

"Hmm."

"But still desiring affection and thirsting for connection, you waste your golden time. Be firm , be steadfast. In the end, the memories that pass will be forgotten, and your time is far too precious for that."

They say that the act of training martial arts means studying, and spelling 'study' in Zhongyuan characters turn it into 工夫 (Gong Fu).

In other words, he was nagging her to study instead of playing around.

And originally, being nagged would generally provoke irritation.

Qing too, suddenly felt irritated.