\chapter{It Seems You're Upset (5)}

The Absolude Sword Walls were the sword marks left by Heavenly Martial Emperor.

Qing observed the marks and acquires the Movements.

However, when Qing stepped in, the hologram of Heavenly Martial Emperor does not pop out to have a conversation.

In other words, when others saw Qing, all they see was a young master standing blankly in place, staring into space without focus.

"Here is the Sword Wall—"

"Shh."

As the Elder was about to introduce the Absolude Sword Wall after they all arrived, Ji Yun Zhenren stopped him with a finger held up to his lips, then pointing again at Qing.

Seeing Qing staring vacantly at some distant point, the Grand Elders pursed their lips tightly and become silent.

In fancier terms, it could be said that Qing entered a state of trance, having realized something the moment she looked at the marks.

For a moment, the Elder swallowed his admiration, but then there's a sudden surge of something.

\textit{What kind of impudent attitude is this from you, Ji Yun, towards someone as esteemed as your martial uncle?}

\textit{Are you trying to match me in hierarchy just because two of us were aging together?}

This was the power of time, exhibiting the remarkable insight of the elder.

Indeed, Ji Yun did had those thoughts.

Whether he was a senior or a martial uncle, they were all old. What can you do when the passing years was so relentless?

There was a threefold difference between a ten-year-old and a thirty-year-old, but only a twofold difference between a twenty-year-old and a forty-year-old.

Since there was negligible age gap betweem sixty-year-old to ninety-year-old, can't they just be friends?

At that moment, everyone's head suddenly turned as if a sense of pressure or danger was sounding an alarm.

The sound of a sword being drawn from its sheath.

Everyone's attention was drawn to the back of the figure, who was holding the sword tightly, along with the sound of the hem of the clothes rustling.

And the elbow, released with the determination of a taut bowstring, drew a horizontal trajectory.

Moments later.

Swish! The slender cypress trees that had been cut once again began to tremble, their branches bucking against each other.

Dozen, maybe hundreds cypress trees had started to tilt en masse.

Some tilted to the left, some to the right.

All timbers swayed in all directions at once, east, west, south, and north, filling the air with the sound of cracking and breaking.

"Whoa…"

In the meantime, Qing let out a long breath.

Her once dull green eyes began to sparkle as she surveyed the fallen cypress forest.

The disarrayed forest startled the monkeys, who screeched and leapt away, while the rustling of birds fluttered around.

Qing's pupils trembled slightly.

\textit{Isn't this environmental destruction…?}

The other Sword Walls might feel wronged.

It's not like they care about being called mere stones; those ancient, time-honored rocks didn't complain when they were split open, jabbed, or pierced through, but here they suddenly looked stunned just for having a few trees toppled.

However, humanity was inherently fickle.

In the meantime, the slow claps echoed.

The fierce voice of Ji Yun Zhenren resonated.

"Indeed. Excellent. To blow away the forest with a single strike, the swordsman of a generation resides here!"

Qing's expression became ambiguous.

\textit{Is that a compliment?}

Anyone who saw and heard the slow tempo of the clapping and his words would say it seemed mocking.

Yet, Qing decided to take it as a compliment.

Because it was Ji Yun after all.

He often mixed his words, unable to distinguish between what to say and not to say…

"What is the name of that extraordinary Movement?"

"It's Nine Solitary Swords Fourth Movement, Severing Ties, Cutting Love."

From somewhere, sighs of 'Ah' escaped.

It was the heartfelt gasp of the Grand Elders, shocked by the Fourth Movement, as they were secretly hoping that the Diancang's Movement ranked at Ninth, as it was still unclaimed. Or at least the Sixth, the next highest spot on the remaining Movements.

"Hmm."

Ji Yun seemed to ponder something deeply, then his eyebrows furrowed.

\textit{What is it? Isn't it a compliment?}

\textit{Was that elevated tone a sarcastic remark about how well I destroyed their forest?}

However, Ji Yun had been purely admiring it out of genuine curiosity.

It was just that there was a separate reason for his frown.

"Hm. I didn't realize Senior Heavenly Martial Emperor was a person who nag."

"What do you mean?"

"To disconnect and sever real-world ties. Why would someone so busy come all the way to this remote Dianchang Mountain to leave such a message? If that's not nagging, then what is?? Like saying to stop wandering around and focus on training."

That was the remarkable insight of a martial artist who had reached Profound Realm.

While Qing was marveling, Ji Yun continued explaining.

The criticism that Diancang was too secular had long since been expressed, even before Heavenly Martial Emperor's reign.

Even inside their sect, it was often brought up in discussions.

Among those secular traits, the Drifting (漂周) were part of that.

As it belonged to a territory associated with an entirely different country, Diancang maintained unique traditions differing from Zhongyuan, where disciples one day must venture into Jianghu and and obtain one of three things to pass on to the sect.

Either defeating wicked forces to retrieve their weapons or defeating renowned swordsmen to obtain their swords.

Of course, it was also possible to resolve things peacefully by bringing talented children back.

"However, if we were to be asked why Diancang became involved in the secular world, it was because the monks back in the Dali Kingdom were originally very proud beings. Are you aware that the teachings of Buddhism broadly divided into two major schools?"

The Mahayana school argued earnestly to disseminate teachings to save unfortunate beings.

The Hinayana school asserted that after eons, the Tathagata already promised guidance, so it would be best to leave suffering beings alone and focus on their own cultivation as they were too overwhelmed.

Dali Buddhism clearly belonged to the latter, and even the royal family was its devout followers, neglecting the welfare of the common people.

This was the actual reason why the elders of Diancang had grown frustrated and thus acted practically.

"To put it bluntly, Diancang's disciples aimed to be Mohe Geluo, so without understanding this backstory, it's easy to see Diancang as abandoning training and only obsessed over worldly fame or money."

Mohe Geluo, alternatively known as Mahakala, originally belonged to the deity Shiva from Tianzhu, but was absorbed by Buddhism and transformed into a protector guarding the Buddha from evil.

"In any case, I shouldn't have come watching. The Movement itself looks good, yet we have our techniques of the Light Splitting Sword ourselves, so it's not particularly necessary?"

A shocking statement from Ji Yun Zhenren.

He declared that the Movement of the Absolute Sword Wall was not particularly needed!

If the Heavenly Martial Emperor, who had gifted the Absolute Sword Wall to his juniors at Diancang as a means to sever their attachments, heard this, it would surely stir a storm of indignation.

But Qing thought, just let it be.

\textit{Rather, speaking of the Light Splitting Sword.}

Qing looked for it, and found Light Splitting Thirty-Six Swords\footnote{分光三十六劍; Fan-guang Sanshiliu Jian}. Purple border.

\textit{As expected, Nine Great Sects are overflowing with Purple Border martial arts.}

Diancang's Sun-shooting Sword Technique was famous for its extreme aggressiveness and speed, but even without that, Diancang Sect was a prestigious sect possesing many Divine Arts.

The Light Splitting Sword also belonged among those renowned Divine Arts, deriving its name from splitting sunlight that pierces the cracks in the clouds, suggesting its swiftness.

Diancang's other Divine Arts included the Sun Piercing Spear\footnote{貫日槍法; Guan Ri Qian Fa} which pierced the sun, the Sunset Dao Technique\footnote{落日刀法; Luori Dao Fa} which split the sun, and One Yang Finger, which emit sunlight from the fingertip.

Notably, the One Yang Finger\footnote{一陽指; Yi Yang Zhi} technique was so powerful that even the deathray of Heavenly Demon Finger must yield against it.

\textit{It seems like everyone is obsessed with the sun.}

Descendants of the Hou Yi who conquered the sun, that would be the Dianchang Sect.

Qing looked at Ji Yun Zhenren.

After observing Ji Yun Zhenren for several days while Dianchang was gathering the Grand Elders, Qing found him to be quite a laid-back individual.

To put it nicely, he was laid-back. To be blunt, whether he was practicing or not, he was always lying down somewhere, sitting down, drinking, carving Buddha statues, or just playing and eating.

If Heavenly Martial Emperor's claims were true, then Ji Yun Zhenren, who had reached Profound Realm, should be the one who cultivated the most diligently to reach higher realm.

Wasn't he someone who had been directly exposed to the rebuke Heavenly Martial Emperor, just as much as Qing herself?

To that, Qing cautiously spoke up.

Ji Yun Zhenren was not even her master, and it could be a quite sensitive question.

"By the way, why did you start learning the sword, Ji Yun Zhenren?"

"Huh? I was excited because they said they want to teach me. Of course, who wouldn't want to learn if someone was offering to teach?"

"Really?"

"I was a farmer's son, and as farmer sons tend to do, I thought I'd just die digging into the earth like that. I didn't think I could leave home and live in this dangerous world.”"

At that time, the martial artist of Diancang appeared and invited him, saying he had potential to thrive within Diancang.

Living a life merely turning over dirt, or live as a Diancang martial artist with great techniques.

"Of course, I chose the latter, no? What fool would refuse that? Naturally, I was excited to follow along. However, while learning, I noticed martial arts aren't that difficult. I merely did what I wanted and came this far. What's so great about Profound Realm? It's a place you can reach with just a little talent, but the road ahead is long. Martial arts truly begin at Profound Realm. Everything before that are merely warm-up exercises."

The elders, who had been listening, found themselves crying internaly.

That 'just a little talent' was precisely the thing that prevented many from reaching the remarkable heights they yearned for.

They suddenly became lifelong practitioners of mere warm-up exercises.

Yet saying anything felt like confessing to have no talent at all, and merely hearing it ignites discontent…

However, it was something that usually happened whenever Ji Yun opened his mouth, and now even the elders were just used to it.

"Severe ties, cut love. While those words imply cutting attachments, if you immerse yourself in severing worldly ties, wouldn't that also signify being obsessed with that severing itself? Thus, you too needn't bear any significant burdens."

"Burden?"

"Being the youngest to reach Harmony Realm must surely weigh heavily on your heart. Why, if you die old still in Harmony Realm, what would the world say? They'd laugh at you, saying you were a Heaven-sent genius who couldn't even reach Profound Realm, and ultimately died a mundane person."

Ji Yu Zhenren dropped a bombshell!

'Harmony Realm?' 'Is she really at Harmony Realm?' 'What do you mean Harmony Realm?'

In an instant, the Grand Elders exchanged glances, their expressions stunned at the thoughless revelation.

'How old is Heavenly Blossom Sword this year?' 'Isn't she just a bit over twenty? Then shouldn't her realm kept secret?'

Nonetheless, being Grand Elders, it was straightforward to understand why one might conceal the truth about the realm attained at such young age.

\textit{More than that…}

\textit{Now that I think about it, shouldn't we sending adept disciples to the Half-Saber-something?}

\textit{Rumor has it that it was a secret training gathering of top martial artist formed by Heavenly Blosom Sword.}

Regardless of that, Qing scratched her chin.

\textit{Hmm, I never had such a thought.}

\textit{Now that I hear it, it makes sense.}

\textit{There was such a saying back then too, mockingly comparing it to a projectile that flies by propelling itself with water.}\footnote{Water Rocket Theory, a League of Legend meme. Basically saying shit about how Faker, a LoL professional player, is out of his prime.}

\textit{It suddenly strikes me that even Master expected that the Zenith Among Women would prove to be the Greatest Under Heaven, but now I feel a new burden growing.}

"Therefore, do as your heart desires. If you wish to train, train; if you want to play, go play; if you want to eat, eat. The most dangerous arrow is the one shot without a purpose. Even if others regard it as a blind arrow, to me, it stands as the sharpest one."

Ji Yun Zhenren wore a mischievous smile.

Even at his middle age, his boyish charm radiated. As the saying goes, a man remains young no matter how old he gets..

In the Dao De Jing, Lao Zhi mentioned 復歸於嬰兒 meaning that those who achieve the Way return to their childlike essence, just as Zhuangzi spokes of 者不失其赤子之心, great individuals not losing the heart of a child.

"And if you follow your heart, later on, even if you reach places you didn't originally intend, you won't have any regrets."

Qing pondered this quietly.

\textit{Severing ties and cutting love. Hmm, while that may not have been the Heavenly Martial Emperor's original intent, the notion of cutting off attachments is true.}

\textit{Something, I think I understand, hmm, I feel like I'm grasping at something.}