\chapter{It Seems You're Upset (4)}

"Ah, no, that's not it, not at all."

Qing hurriedly retracted her words.

Saying "no" was too strong of a phrase.

"If you think about it, isn't martial arts ultimately something you train for the sake of living?"

"Huh?"

"Why, even in the Dao, they talk about the living sword\footnote{活劍; Huo Jian}, and on our side, at least, we speak of self-defense. It was said that to govern oneself, manage one's family, and bring peace to the world, one must first protect oneself."

"Hmph. You're quite the talker. So?"

"So, it seems martial arts should be a means, a tool, right? The way to protect myself and those I hold dear. If I end up abandoning those who are precious to me while learning such martial arts, wouldn't that be putting the cart before the horse…?"

Just as Qing's heart had been, to her, martial arts was a means of protecting herself and also those close to her.

For that reason, she would be satisfied as long as her martial arts were enough for self-defense and protecting her loved ones.

But the problem was that it wasn't easy.

To be precise, the problem lay in the combination of this primordial ancient Zhongyuan, the cosmic mysteries of Qi, and the overlays of the Status Window.

While she was somewhat getting used to the existential crises, she was sure in the notion that this world was not merely a some artificial, fabricated virtual world.

But what if one day she opened her eyes to find himself back in that narrow corner of a room on the outskirts of of that industrial complex?

The so-called 'damn it, I had this dream'.

And it wouldn't be all that strange.

What happens once can happen again, and just as he was dragged one day, it wouldn't be odd if she returned one day.

To protect herself, she would seek to settle things with the Status Window, but it was an issue that was far too lacking in the realm of Hwa-gyeong.

However, the Heavenly Martial Emperor scoffed.

"With a mindset like that, learning martial arts will lead to a chaotic Wulin. Where do you think you are making such suffocating remarks?"

"Why, what's wrong with that?"

"What is a tool? If one has a sharp knife, they will want to try cutting something. Even a common woodcutter, upon receiving a new axe, will be eager to climb a mountain at once. But what if a martial artist does that? They were so eager to wield their martial arts that they were easily caught up in trivial matters! Just as a river flows when trying to launch a boat, they'll see the moment and shed blood"

顺水推舟 (Shun Sui Tui Zhou). 'Push the boat along the flow' was a saying in Qing's homeland, meaning it's like being slapped when you want to cry.\footnote{The original meaning is 'to take advantage of the situation'; the author was being sarcastic.}

"The mindset of regarding martial arts as a means to an end is exactly the mindset of a Demonic Adept. Well, come to think of it, you're a Demonic Adept, aren't you? As they say, you can't help your innate nature. And come to think of it, you're no ordinary Demonic Adept either. A Demonic Adept among Demonic Adepts, a truly Great Demonic Adept—"

"Please, don't say that."

"Hmph. If one possesses a good sword, they want to wield it. Should it be sharp, even if it's unnecessary, they will be delighted to swing it around. Thus, with the martial arts they learned for self-defense, they start using it to bully others, and as you said, they begin living off of martial arts, wrongfully taking from others instead of working to sustain themselves. There's no bandit as such in this world like them."

The eyes of Heavenly Martial Emperor burned fiercely.

To put it nicely, that gaze embodied an unwavering conviction, while a negative view could interpret it as a sort of madness.

"Martial arts should not merely be a means; it must be a goal. It is the ultimate aspiration where a person can surpass another, that uncharted realm which no one has conquered until now. For a true man, it is the gentlest yet greatest ambition that cannot be endured."

"Huh?"

"What? What ambitions are worthy of a man possessing greatness? If one targets the world, there will only be chaos and bloodshed, countless mortals spilling their blood in the process. Should one aim to become the world's number one merchant, they will exploit countless commoners to achieve that wealth. To grasp the status of the world's best will require building a throne upon the corpses of the fallen. And all these things are what martial artists do, there's a reason why blood and tears never dry up in this world."

But what about one's own cultivation aimed at observing the end of martial arts?

Simply achieving improvements and wishing to advance, it was the greatest challenge that has never been accomplished by anyone, and it was the gentle challenge that does not harm others.

"Martial arts were originally a form of rigorous training in the Buddhistic way of Tianzu. When Damo saw this in Tianzu, he thought it was truly wonderful and spread it throughout Zhongyuan. Hence, martial arts should originally be a practice for reaching nirvana through self-completion, yet you people of mere mundane desires wield them for personal wealth."

"Hmm."

That was a perspective Qing had never heard.

\textit{It sounded plausible upon listening.}

\textit{After all, a master of virtue like Damo wouldn't have spread a technique for killing in the past.}

\textit{There were mystical Qigong among the practices of Tianzu, which Damo must have viewed and brought back as supplementary teaching to the Buddhist scriptures in Zhongyuan.}

\textit{Thinking like that, it meant the roots of martial arts wasn't the the art of killing or even self-defense, but was a method to reach nirvana.}

\textit{But still…}

Qing cautiously spoke up.

"Well, not everyone in the world needs to have such lofty dreams. Some people may simply wish to live happily with their family and friends."

Since Qing already the best in the world (in her own opinion), she had no interest in reaching Nature Realm or aiming for ascension through cultivation.

At that, Heavenly Martial Emperor snorted again!

"What weak-minded talk is this? If born a human, one should bear grand thoughts and take actions driven by tremendous ambition. A life unable to fulfill such a purpose merely reflects pitiful self-satisfaction and is a worthless existence."

Suddenly, the image of the Yue Maiden crossed Qing's mind.

The current martial arts in Zhongyuan most likely root back to the practices found in the Tianzhu region.

But wasn't the earliest martial art was the Yue Maiden's Yue Sword, which existed one thousand years before Master Damo brought martial arts from Tianzu?

Yue Maiden's Sword was nothing more than a stick fight played by a nameless child running around with monkeys.

Moreover, even though the Yue Maiden possessed the only martial arts of that time, akin to the absolute being of that era, what she truly desired was to live happily under peaceful skies with her beloved.

It wasn't some lofty goal of conquering the world or ascending to the heavens.

Unfortunately, the ending of the Moon Maiden was tragic

"It's not worthless; it's just ordinary. Moreover, it's natural. Some might find happiness in achieving such goals, but ordinary people simply enjoy life, seeing nice things and eating delicious food. As long as they don't cause harm to others, isn't it enough for them to be happy? Not everyone needs to achieve something grand."

Yet again, the Heavenly Martial Emperor let out a sneer.

"Hmph, that's just an excuse for those who lack the confidence to achieve something in life. In the end, it's a pitiful state because they believe it's impossible and have long given up."

Qing exhaled deeply in her heart.

It's always like this.

It's common for those who have achieved something to look down on those who have not.

Successful wealthy individuals deem the poor as pathetic, and academic authorities consider the ignorant as foolish.

Or, in Big 3 weighlifting, like how those who lift weights to about four hundred pounds looked down on either overweight people or those who were thin.

But being overweight isn't a sin nor was it something that must be shed, as long as one was satisfied and happy, isn't that enough?

Even if they wish to live like that, although rising to diabetes wouldn't bring them joy, they must at least manage themselves to some extent.

\textit{But isn't this also belittling those with abundant fat? 'Tsk, tsk, you're going to die tomorrow, but you don't anything about it…'}

\textit{As long as they are happy, that would be enough, right…?}

At that time, the sound of a tongue-clicking accompanied by displeasure snapped Qing back to reality.

"Tsk, tsk. How did I end up entwined with this girl? That's enough. I'm leaving as there's nothing to do."

"Ah. What about the Movement?"

"Didn't you hear? I'm saying I have nothing to do. I'm not begging you with tears in my eyes to learn anything. What's the use of teaching a lifetime of study to someone who only wishes to live an ordinary life? If I were to choose someone to continue my studies, the entire world would line up and swarm in like locusts, filling a city."

Qing thought.

\textit{Ah, he seems to throwing a tantrum.}

\textit{It appears that in the spur of the moment, I may have crossed a line.}

\textit{I lost enthusiasm, so he's overreacting.}

\textit{But hmm, that's that, still?}

"But, Elder, is this really my own Imagery? So where's the Movement? No, um, if it's as you said, I saw the sword marks and read its meaning, and you said you are an illusion created by my own imagination, and now you're suddenly say you'd teach me?"

Qing narrowed her eyes.

\textit{This isn't the Grand Emperor Wuqing, this is undoubtedly the Grand Emperor Wutian himself!}

Yet, the Heavenly Martial Emperor remained indifferent.

"You should ask your heart. Since you disliked my Movement and were reluctant to learn them, it's only natural you wouldn't want to learn from something you conjured in your mind."

"That's not true. I absolutely want to learn!"

"The true intentions of a person can sometimes be exceedingly difficult for them to recognize, even by themselves. You see the source of the Movement from the sword marks and feel its Imagery, the ruthlessnes of this disconnection from destiny; it only reflects the indifference within you. Doesn't that mean it doesn't match with you?"

Qing scratched the back of he head.

\textit{Ah, lately, I have been having such thoughts.}

\textit{What is the correct one? Is he Grand Emperor Wutian or Grand Emperor Wuqing?}

Then the Grand Emperor Wutian let out a deep sigh.

"Ha, you see. Formless Skill was not a legacy, it's but a shortcut. Did the great predecessors who first reached enlightenment rely on such methods? Surely not, for they opened the new horizons of learning unique to their paths, revealing an unknown world for future generations to tread upon."

"Formless Skill, you say?"

Qing questioned, but the Grand Emperor Wutian spoke as if he hadn't heard.

\textit{Ah, what is this atmosphere?}

"The essence of martial arts is to forge your own sword within your heart, tailoring it to your own needs. Only you can shape your own sword, and even if you like someone else's sword, it won't become your own."

"Wait, you're already going in-"

"Formless Skill was nothing more than the trivial art of looking at answers and imitating them. The knowledge you posses is by no means your own."

At the same time, Qing drew her sword.

No, the sword was moving on its own.

Wouldn't her hand move on its own to grip the sword, press it against her chest, and extend it out over her other forearm?

"Even a perfect imitation will work. But now that you've grown thick-headed, you seem to be having second thoughts. So, even if you reads the sword marks at the next Absolute Sword Wall, you probably won't be able to imitate the Movement."

"Oh, then-"

"So, either you must be determined to dedicate your life to truly transcendence through study, or you must harbor within your heart a fiery furnace capable of melting other people's swords and refining them into your own. Only then can you reach the next stage of study of the Nine Solitary Sword."

At the same time, her arm snapped out.

The trajectory of the sword extending horizontally to the ground.

\textbf{Solitary Nine Swords. Fourth Movement.}

\textbf{斷緣切愛. Duan Yuan Qie Ai. Severing Ties, Cutting Love.}

The cruel heart that regards all relationships as mere burdens and cuts them off sharply divides the world, the point where heaven and earth meet.

Now the world was divided in two.

However, this was a task that a being standing between heaven and earth must naturally accomplish.