\chapter{Tang Clan's Paper Flower (9)}

Qing judged it as the Tang Clan's second victory, but that wasn't actually the case.

In fact, it was their third victory.

This was because the Imperial Censor had presented a dilemma of death by blockading the Tang Clan - either starve to death or die for treason.

What came back was food waste thrown out ostentatiously outside the gates and walls.

Strangely enough, it always fell exactly where the soldiers or guards were standing, and the Tang Clan's official stance on this was:

‘Eh? Why are you standing there?'

The Imperial Censor, with his eyes rolled back in anger, went around turning Chengdu upside down trying to find the Tang Clan's supply line.

But how could that be easy?

Even from the perspective of Zhongyuan people, Chengdu had been a prosperous ancient capital for over two thousand years, a land where dynasties had nested.

In other words, there were already plenty of passages dug by ancestors, to which the Tang Clan had added and improved underground passages over hundreds of years.

It was not a sacred realm that could be invaded by the shallow wisdom of humans who had lived a mere fifty years.

As such, six Embroidered Uniform Guards and thirty soldiers who found and entered three secret passages became eternal guests who would never return.

Because the discovered passages were turned into poison fields, even the corpses couldn't be retrieved. Thus, the expression that they had become wanderers who could never return was quite accurate.

The Tang Clan's official stance on this was:

‘Oh, we collected and disposed of the poison sprayed by the cat. Why are you passing through the garbage dump?'

Meanwhile, two more red dots were added to the Tang Clan's map of Chengdu, meaning they had discovered two more artillery positions.

Victory No. 4 for the Tang Clan.

After this series of defeats, the Imperial Censor realized that he was no match for their shamelessness, rudeness, and local infrastructure.

"Damn these bastards."

The Imperial Censor gritted his teeth.

The option of taking out false evidence under the guise of a search had gone down the drain forever due to the rampage of the invincible cat with Invulnerability of Ten Thousand Poisons

He couldn't starve them to death either.

What remained was the strategy of provoking them to strike first.

Just one hit. One hit would be enough.

Even a light tap on the back of the hand would do.

After that, he could shout 'How dare you harm the Emperor's army! You truly are traitors!' and fire cannons, push in soldiers, and turn the place into a wasteland.

So the Imperial Censor racked his brains, thinking about how to anger these traitorous Tang Clan bastards, how to piss them off.

Finally, he found a point that the Tang Clan couldn't endure, what could be called their trigger, and smiled with satisfaction.

Thus dawned the fifth decisive battle on the fifteenth day.

The Imperial Censor, who boldly entered through the main gate of the Tang Center, which remained shattered from lack of repair, scanned the Tang Clan elites blocking his way.

And he quickly found a weakness among them.

Of course, anyone with eyes could find it quickly, because there was a peerless beauty in place, around whom the surroundings suddenly brightened and flower petals seemed to flutter in an illusion.

The Tang Clan's precious daughter, the Speaking Poison Flower Tang Lan-ah.

They say she was raised with abundant love from the family and considered her their pride.

Could they really endure if such a precious flower was insulted?

This was the trigger of the Tang Clan that the Imperial Censor had found.

"Listen here, Imperial Censor. Let me tell you in advance, actually, last night, a mischievous wild cat caused havoc in the warehouse-"

"That is enough now. I have long known that you bastards are beasts who cannot be reasoned with."

"Then shouldn't you just turn back without wasting your breath?"

At this, the Imperial Censor smiled vilely.

"This time, I came to find a way for you traitors to live out of pity."

"A way to live?"

"The national law is strict, so the crime of treason is a capital offense that will exterminate nine generations of the family. Thanks to this, all those with the surname Tang from Sichuan will die without exception. However, if you can still leave that blood behind, it would not be complete annihilation of the clan, would it?"

Tang Touzhong's complexion darkened for a moment.

He wondered what kind of nonsense the Imperial Censor had prepared to have such a long introduction.

However, his facial muscles immediately tightened at the Imperial Censor's next words.

"I shall do you the honor of taking that passable wench instead of killing her and using her as a slave. Even if she happens to get knocked up, I shall not necessarily abort it to cut off the lineage, so you could preserve the blood of dirty traitors. How does that sound? Does it not seem like a good idea?"

Tang Touzhong's face contorted severely.

The Imperial Censor's face brightened in proportion.

Moreover, upon thinking about possessing the Most Beautiful Woman in Sichuan, he suddenly felt excited as blood rushed to his nether regions.

"Even if it is the blood of dirty traitors, once the merciful Imperial Censor shares his seed, it will be half a loyal subject and half a traitor's blood. Would that not be enough to use as slaves for generations?"

"If you do not watch your words-"

"If I do not watch my words? Are you daring to threaten an official carrying out His Imperial Majesty's jade command? Is this not the behavior of traitors to the world?"

"…I am just saying it would be better to close that vulgar mouth of yours."

Tang Touzhong weakly stepped back.

"You there, wench. Do not just stand there like a mute and show some skin. Right, I should check if you are still a virgin too. Then again, with a face like that, I wonder if any man would have left you alone. That dirty blood must have been writhing in lust like a whore every day."

Tang Lan-ah's face turned pale.

"What, feeling wronged? If not, lie down and spread your legs right now. After all, would it not be easier for people to check with their eyes in regards to whether your chastity is intact?"

Tang Lan-ah, who had studied medicine and become a master of toxicology at a young age, was intelligent.

She knew that in this situation, she had no choice but to endure the insults pouring down, as it was just a matter of rank and rudeness.

Just as Tang Lan-ah's eyes were moistening and her hands were trembling slightly…

Suddenly a weight pressed down on her head, and a semi-transparent membrane-like object draped over her, creating a layer of fence from the world.

"Excuse me, Imperial Censor? Elder?"

The Imperial Censor's eyes widened.

The veiled woman who had mentioned food waste last time had passed over what she was wearing, revealing another peerless beauty underneath.

Qing stood demurely and raised her voice.

"It has been said since ancient times that children are mirrors of their parents, so don't people's words and actions ultimately come from their parents' conduct?"

"Was there such a saying?"

Of course, there was no such saying in Zhongyuan.

But as soon as he heard it, he immediately understood what it meant.

In Zhongyuan, there was a saying that children resembled their parents.

Similarly, in the Mingxin Baojian\footnote{lit. 'bright heart-mind precious mirror', a collection of aphorisms and quotations form the Chinese classics and other works}, it was said that where cucumbers are planted, cucumbers grow, and where beans are planted, beans grow.

Furthermore, Lord Mengchang, who served as the Chancellor of the State of Qi during the Warring States period, said that Generals come from Generals' families and Chancellors come from Chancellors' families.

All of these meant that children take after their parents, expressing a universal human nature that all cultures of humanity have sympathized with since ancient times.

"The words that the Imperial Censor is saying now are vulgar and vile, something only the shittiest mongrel under the heavens would say, but since the Imperial Censor's parents are precisely that shitty mongrel, you've just inherited their speech and behavior, so we shouldn't blame the Imperial Censor, right?"

"What-"

"It means if you don't want to smear shit on your parents' faces, you'd better watch that mouth of yours. Though we've already known the level of your family education, since you've already smeared shit all over your parents long ago."

Currently, there was no one in the world who could match Qing in insulting parents.

This was because in Zhongyuan, insulting someone's parents was equivalent to challenging them to a life-and-death duel, saying 'Let's see who lives and who dies today'.

However, having lived in a society of unfilial children who casually inherited parent insults, Qing's study in this area had already reached a realm worthy of discussing the title of Greatest Under Heaven for this particular field.

"You, you bitch…!"

"Ending every sentence with 'you bastard,' 'you wench', ‘you bitch'. I guess that's how your parents address people?"

"You dog-like-"

"Imperial Censor. Please calm yourself."

At that moment, the third-in-command of the Embroidered Uniform Guards, the Guard Assistant Commander, standing beside him, gently tapped his shoulder and intervened.

The Imperial Censor glared at Qing while panting, gradually calming his ragged breathing and regaining his original composure.

Just then, there was a subtle touch on Qing's fingertips, which soon climbed up to her palm, leaving behind something hard before slipping away.

It was a familiar size, one of Poison Grandfather's poison bottles.

Only then did the Imperial Censor open his mouth again.

"Your words are laughable. How dare traitors call themselves people? My parents always said that traitors are like ungrateful beasts, so I am just doing as I was taught. Courtesy is only extended to humans."

\textit{Is that really all you can say after all that?}

Qing put strength in her eyes, making a round-eyed surprised expression as she asked back.

"Huh? Excuse me, but may I ask which of the Imperial Censor's parents is the beast?"

"What?"

"No, just now you were talking about sharing seeds with our Lan-ah and whatnot. But you said traitors are beasts. Then, did you inherit the hobby of mating with beasts from your parents too?"

"Wha-"

"AH!!! NOW THAT I'M LOOKING AT THE IMPERIAL CENSOR!! I CAN TELL ONE SIDE IS A PIG! DID YOUR FATHER! MATE WITH A PIG! AND GIVE BIRTH TO YOU, OR DID YOUR MOTHER! MATE WITH A PIG! And give birth to you? Well. Either way, you're a half-human half-pig fat fuck!"

Qing raised her voice, cutting off the Imperial Censor's words and rapid-firing her own.

Qing's volume had already surpassed human limits, so amidst the thunderous sound, her beautiful voice rang out clearly beyond the walls of the Tang Clan's main gate without becoming shrill.

"Shut-"

"WOW!!! EVERYONE LOOK AT THIS!!! HEY YOU MIDDLE-AGED MINIONS OVER THERE!!! DID YOU ALL JUST HEAR THAT!!? THERE'S A MONSTER CHILD HERE! BORN BETWEEN!! PARENTS WHO MATED!! WITH PIGS!! LOOK AT THIS IMPERIAL CENSOR!! LOOK AT THIS ELDER!! HOW CAN SUCH A THING EXIST IN THIS WORLD!!"

"You-"

"WOW!!! THEN CAN WE CALL THE MASTER BEDROOM A PIGSTY!? COME TO THINK OF IT, THE IMPERIAL CENSOR'S MOTHER!! IS EITHER A PIG!!! OR MATED WITH A PIG!!! EITHER WAY, SHE'S JUST A SOW OBSESSED WITH BEASTIALITY, RIGHT?! IT MUST BE SO NICE!!! TO HAVE A SOW!!! AS YOUR MOTHER!!!"

"You-"

"WAIT!!! WHAT?!? ARE YOU EMBARRASSED!!! ABOUT YOUR MOTHER RIGHT NOW!? WHY CAN'T YOU SAY IT PROUDLY? IMPERIAL CENSOR!!! YOUR MOTHER!!! MATED WITH A PIG!!! IMPERIAL CENSOR!!! YOUR MOTHER!!! IS A DIRTY PIG BITCH!!! UWAAAAAAAAAH!!! HOW CAN SUCH A THING HAPPEN!!!"

The Grand Clan Lord who was listening trembled.

By tonight, the shocking rumor about the Imperial Censor's mother's infidelity would spread throughout Chengdu as if it were fact.

And he could clearly see that new facts circulating in Chengdu would spread throughout Sichuan, and within a year, the everything under the heavens would accept it as truth.

The Imperial Censor, as the head of the Censorate, belonged to the second rank of high officials, so the family that produced him was originally among the most prestigious of prestigious families.

However, now their downfall was clearly visible.

Immediately, they would be despised and cut off from relationships up and down their faction (Guanxi), and for the sake of the Imperial Family's face, they couldn't keep someone with such an indecent rumor in an official position.

"Hoh. My, my. It seems this old man has finally found the ultimate poison that would fill the rest of one's life with pain through humiliation worse than death."

It was a scene where the ultimate poison the Grand Clan Lord had dreamed of was being realized with just a three-inch tongue.

How could one not tremble with emotion?

"It has no substance, cannot be prevented from poisoning, and does not even need to be administered. Indeed, that gossip is truly the very definition of Formless Poison."

The Grand Clan Lord, speaking as if he had gone senile, took out all the poisons he had personally modified and swept them into a separate poison pouch.

It was a gift bundle for Qing.