\chapter{Tang Clan's Paper Flower (15)}

Qing quickly shook the blanket.

With a Pararak sound of Inner Qi shaking the cloth, wooden pieces clattered Dadadadak.

"Fi- Fire Bombs! Thunder bombs!"

"Huh?"

"Hey!! Danger!!"

Tang Lan-ah threw herself towards Qing as if diving into water, and as they tangled together, they rolled off the bed and tumbled into one body.

And then, BOOM!!

Along with an ear-splitting explosion, all sorts of sounds of things breaking, tearing, and embedding occurred at once, causing such a commotion that their ears became muffled and there was a slight ringing.

Being a military veteran, who was ironically also a young beauty, Qing's mind snapped awake at the massive explosive sound of gunpowder.

\textit{Artillery fire!? This is artillery fire, right!?}

"What the hell, since when did Wulin have time fuses!?"

Unfortunately, these were the same Chinese people who made the act of burning things part of their national spirit and turned their history and ancestors into charcoal.

Even going so far as to have children take the lead in beating their parents to death, claiming parents were the evils of the old era - the Red people who carried out ruthless sacrifices for the greater good while laughing!

So how could the Chinese, inventors of the ultimate material for burning - the original gunpowder - and pioneers of firearms, not have come up with the simple idea of shooting bombs from afar?

Moreover, the Imperial Family had been grinding their teeth to eradicate Wulin Practitioners, and the culture of artillery crews working overtime without nights off had already been going on for over a hundred years.

"We need to get out of here right now."

Knowing about artillery fire and experiencing it were two different things.

Qing, who was terrified and about to rush out immediately, had her wrist quickly grabbed by Tang Lan-ah.

"Clothes! Put on clothes first!"

"We're about to die from artillery shells! What do you mean clothes?"

"Hurry!!"

And so, while the earth kept rumbling Boom Boom and cannon fire vibrated near and far, the two women were moving around, somehow managing to put on clothes.

With a Crack, another shell broke through the wall, and as they jumped and lay flat on the ground, BOOM! It felt like the whole world was shaking-

Creeeak.

Suddenly, all the woodwork twisted at once, making an ominous sound.

"What are you doing? It's collapsing! We need to get out quickly."

"Poison! We need to take the poisons!"

Tang Lan-ah was busy opening this drawer and that drawer, sweeping their contents into her bosom, stuffing them into the ancient belt on her thigh, pushing them into the armband on her forearm, busily arming herself.

And then a Crack, followed by a sound of rupture that chilled the chest, Qing immediately tucked Tang Lan-ah's waist under her side and charged towards the door panel.

After all, it was just a wooden frame covered with paper, a structure that a martial artist's body could easily break through.

"Ack!"

However, since she had tucked Tang Lan-ah under her waist, the luggage's head hit the door before Qing's.

Tang Lan-ah's head, as if it had become a siege hammer, broke through the door with her crown.

After coming outside and putting her down, Tang Lan-ah glared at Qing with fierce eyes while wearing the window frame around her neck like a cangue (the long board criminals wore around their necks in historical dramas).

"Ah, my mistake."

"Tch, forget it!"

Tang Lan-ah threw away the window frame she had been wearing.

Chaos reigned everywhere.

The smell of burning in their noses.

The black smoke billowing up into the night sky, and flames shooting up from the ground.

The sound of Swish Swish cutting through the wind, the clear sound of shells falling near and far, and roofs and walls being smashed to pieces.

And one terrible wail.

"Child! No! My child!"

"Gramps! I'm here!"

Cui Liweng, who had been digging through the ruins of a collapsed annex, quickly approached and felt Qing's arms and legs.

After confirming Qing was safe, he took out a face veil with visible relief and put it on her.

"What do we do now!?"

"Underground! There's a passage!! This way!! Just step where I step and follow me!"

Tang Lan-ah deployed her Qinggong and ran towards the devastated inner part of the Tang Center.

Qing followed behind, crossing over the smashed main gate, passing through narrow alleys, going around burning buildings, and winding through.

And when they arrived near a pond behind a certain building, Tang Lan-ah tapped the ground, crouched down low, and somehow managed to lift up the floor.

"This way, hurry."

Tang Lan-ah said that and then grabbed the ladder attached to the wall and quickly went down.

The question of whether they didn't need to close this lid crossed Qing's mind, but if the daughter of the house owners said so…

As Qing was climbing down the ladder, about halfway down, there was a Thunk sound of the lid closing.

Boom, Boom. The artillery fire heard from underground sounded like long-lasting, giant drum beats.

With each beat, Poof, dirt dust showered down, hitting the brim of the face veil Qing was wearing with a Tododok sound.

Tang Lan-ah, who was bareheaded, just irritably shook her head at the falling dirt dust.

As they made their way through the underground passage like this, a space wide enough to fit about two buildings appeared.

"Grandfather!"

"Ah'er! Child Ximen is safe too! Thank goodness!"

Unexpectedly, the underground cavern had a calm atmosphere.

It was gloomy but not sad, and while they seemed shocked, they weren't terrified.

At the center, the Tang Clan elite Masters whose faces Qing had seen several times were gathered around a large table.

As Qing approached, she saw a familiar face.

Despite his pale complexion, he had a gentle impression, looking just like a bookworm.

"What? Ziyou? Didn't my friend run away?"

"How dare you! Whose safety do you think is at stake to speak so recklessly! Kneel immediately and show your respect!"

At this, a small-bodied woman holding a spear shouted in a loud voice.

Qing blinked her eyes.

"Oing? Why? Whose safety is it?"

"The lord of Sichuan, His Highness Grand Prince Dexian is present, yet you dare to raise your head high and act impudently as a mere martial artist!"

"Oing? Grand Prince?"

"Aht! The weakling, I mean, aht! This girl has committed a mortal sin!!! Please forgive my previous rudeness!!!"

It was a scream-like sound that burst out next to Qing.

When she turned her head, she saw Tang Lan-ah's back, who had somehow prostrated herself on the ground in an angled posture.

In her haste, she hadn't tied her hair, so how violently must she have bowed her head for her hair to spread out straight like an unfurled brush?

Qing looked down at that sight with half-opened eyes.

\textit{This girl… I felt this since last time, but…}

\textit{Isn't she being a bit too cheap with her knees?}

Anyway, while Tang Lan-ah remained motionless like a stone statue stuck to the ground, Qing looked at Ziyou.

"Uh. Um. So you were a Grand Prince?"

Ziyou just shrugged his shoulders with an embarrassed expression.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In chess, why is the cannon usually placed near the palace or close to it?

It was because it was such an important piece.

If so, the Fire Soldiers of the Imperial Army in reality were truly the elite of elites, selected from among the most outstanding Imperial soldiers.

They were not only physically strong but also loyal subjects whose loyalty had been verified, and they were also scholars skilled in mathematics for accurate artillery fire.

Therefore, the defense surrounding artillery positions was not like that of ordinary soldiers; a defense team trained in specific martial arts was stationed together to take charge of their protection.

In terms of Wulin practitioners, they were at the end of the Second-Rate level, able to properly handle weapons, so when they formed battle formations and deployed strategies, it wasn't easy even for Wulin Practitioners to deal with them.

However, among the Ten Noble Clans and the Nine Sects One Union, there was one force with a strange combat capability. Although they were evaluated as insufficient to face Masters, they were infamous for dealing with low-level practitioners.

"Hey, don't you smell something? What is it? It's sweet."

"Peaches! It smells like peaches."

A fragrant peach scent mixed with the cold night air.

"Peaches? It is peach season, but who would be eating peaches in the middle of the ni- Khaak, cough."

The soldier who suddenly coughed up phlegm then rubbed his itchy nose.

"What's this? Blood? Uh…"

At that moment, the soldier staggered and collapsed.

"Hojang? What's wrong?"

"Strange, I feel a bit tired. Why is this happening?"

Then something flowed from his eyes too, bright red blood trickling down his tear ducts.

"Hojang, blood, there's blood! Khek, cough, cough!"

The soldier who had been making a fuss started coughing dryly and suddenly vomited what came up.

"Uh…?"

That's when it happened.

Something about the size of a child's head flew from afar and fell between the two with a Thud, rolling around.

"Damn it! Kheuk, kuk. It's a Poison Bomb! Everyone swallow the antidote powder and cover your mouths with the detox masks!"

BOOM!! Unfortunately for them, it wasn't a Poison Bomb but an explosive bomb.

The shattered metal fragments tore apart the flesh and bones of the two people, and after their eyelids fluttered, the two were no longer recognizable as human forms, just debris scattered across the ground.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Gradually, the sound of artillery fire decreased, and soon the loud explosions that had been tearing through the night completely subsided.

At the command post, the Imperial Censor was furious.

"What is this! Who ordered to withdraw the cannons on their own! Keep firing! We need to turn them into ashes…"

"Urgent report, the First Artillery Battalion has been annihilated."

At that moment, another messenger who had entered the command post hurriedly interrupted.

"It's terrible! The Second Artillery Battalion has been annihilated!"

The Imperial Censor gritted his teeth.

"How is that possible! What were the artillery defense teams doing!"

"Fire Bombs! They say the Tang Clan bastards are using Fire Bombs!"

Fire Bombs were effective even when used by soldiers who hadn't undergone proper martial arts training.

All one had to do was light them and throw them far.

But when used by Masters, they were even more powerful.

Especially the martial artists of the Tang Clan, who were experts in various Throwing Techniques.

Fire Bombs thrown with the subtleties of hidden weapons were practically human artillery, capable of long-distance precision throws even without cannon barrels and gunpowder charges.

"How can a mere civilian clan use Fire Bombs! How dare they! These traitors!"

The Imperial Censor exhaled angrily and went berserk.

The manufacture of gunpowder was strictly prohibited by national law, and violating this was truly treated as high treason.

While the Imperial Censor was having a fit, unable to control his rising anger and stomping his feet, new reports came in announcing the annihilation of three more artillery battalions.

"No! The soldiers bestowed by His Imperial Majesty!"

And only then did the Imperial Censor take a long breath in and exhale deeply.

"No, no. That's right. So the traitors have finally shown their true colors. This is rather fortunate. With this, we can mobilize the provincial army…"

The Imperial Censor decided to think positively.

Losing all the artillery positions was painful, but thanks to this, they had discovered the fact that the Tang Clan had been secretly manufacturing Fire Bombs.

Of course, the Imperial Censor was also aware of the extent of illegal Fire Bombs circulating among civilians, but whether they bought them or made them, it was a matter that could be pushed as treason either way.

No matter how much they were one of the Five Great Clans or peerless Masters, how long could they hold out against hundreds of thousands of Imperial troops?

With the evidence already clear, even Wulin wouldn't dare interfere with the Imperial Family's actions.

That's right, hundreds of thousands, they had hundreds of thousands of soldiers.

One Guard Division had about six thousand soldiers, and there were several such Guard Divisions in one administrative province. If they gathered for wartime conscription, nearly thirty thousand soldiers would be assembled from Sichuan Province alone.

Just by adding troops from nearby Hubei, Shaanxi, and Guizhou, over a hundred thousand Imperial troops could be mobilized.

The Imperial Censor was the head of the Imperial Censorate.

He had the enormous authority to mobilize a province's Military Commander, so once justification was established, he was a very, very high-ranking person with the command authority over a great army.

That's when it happened.

Another messenger pushed through the tent as if about to tear it, leaving urgent muddy footprints.

"It's terrible!"

The Imperial Censor snorted and answered.

"I see. Has the Fourth Artillery Battalion been annihilated as well?"

Losing the artillery positions was painful, but just over two hundred cannons and about eight hundred gunners were like a handful of sand compared to the entire Imperial army.

If throwing one grain of sand gained justification, wasn't it rather something to be glad about?

"That is not it! The Grand Prince's flag, they have raised the Grand Prince's flag! Those bastards have raised the Grand Prince's flag!"

At this, the Imperial Censor's expression completely crumpled.