\chapter{Tang Clan's Paper Flower (6)}

The scene that first came to mind when Qing said she would participate in the strategy meeting was like this:

An impressively made model of a wide view of Tang Clan.

A complex blackboard and papers full of systematic operation plans with first, second, and third tier formations and rotations.

A serious and heavy atmosphere.

And at the end, even a cool speech to raise morale.

However, the reality was a mess.

It was a scene of all the Tang Clan elders gathered around a roughly drawn map, massaging their arms and legs while chatting idly.

\textit{What's this? Didn't they say it was a strategy meeting?}

As Qing tilted her head in confusion, one of the elders looked at Tang Lan-ah with eyes that didn't hide at all how adorable he found her.

It was the kind of look often described as honey dripping from the eyes.

"Ah'er, did you not sleep well? Hoho. It seems you stayed up all night talking with your friend."

At this, Tang Lan-ah awkwardly avoided eye contact.

Somehow, the tips of her ears were bright red.

"Haha, there's nothing to be embarrassed about. Isn't it natural that when making a good friend, you should lie in the same bed and talk endlessly to become true friends?"

The elder seemed to have a different understanding of the reason.

"When this old man was young, I often lay together with friends. When we lay together and talked while looking at the stars, the hardships of sleeping outdoors didn't seem like much. Looking back, those times were truly beautiful."

"So Ah'er should also laugh, cry, argue, and lie down to talk a lot with friends in your youth. Just like Sun Ce and Zhou Yu did."

"Like the Liu Bei's Three Sworn Brothers did."

"How could we leave out Bo Ya and Zhong Ziqi?"

"Guan Zhong and Bao Shuya also shared one bed."

"And Nuo Yao and Ma Li too."

"Hey now, weren't Nuo Yao and Ma Li made-up people?"

"Well, who knows? The names might be different, but it could be a true story heard and written down."

The elders' chatter continued amiably.

Qing took this opportunity to confirm her doubts again.

"So, friends sharing a bed is…"

"Of course. Wouldn't you say it's the first gateway to welcoming a true friend? One should…"

Tang Lan-ah hadn't lied, but she had been deceiving.

It was because of her cunning desire to try sleeping in the same bed with a friend just once, but it could be considered a mitigating circumstance.

In fact, the saying about lying in one bed and covering with the same blanket meant going through hard times together.

Because the family was poor, they lived sharing one bed and one blanket.

How could the bond formed by sticking together through hard times not be exceptionally strong?

Originally, friends who were well-off would use separate rooms even among siblings and not have to bump into each other.

The Tang Clan elders were well-off even as children, so they meant something else.

They were expressing in a roundabout way that the earth was their bed and the sky their blanket, referring to sleeping outdoors together while wandering in Wulin.

Since the elders didn't know about Tang Lan-ah's vicious deception, their sincere words were ultimately a truly genuine attitude.

It was similar to that unique attitude of elders getting excited to answer when young people ask about something they know?

So Qing completely abandoned her doubts.

Instead, she reflected.

\textit{Changming'er must have been very disappointed.}

\textit{Should I sleep together with her when I go back this time?}

\textit{But Changming'er is a minor…}

\textit{How could one share a bed with a minor when the national law was so strict?}

\textit{It could even be a dangerous act of defying heaven and destroying the earth that might bring about a crisis for the world.}

"But what about the strategy meeting?"

"Hoho. The strategy have been established long ago, don't you think? We've always been prepared and on guard against dangers, so if we were to be busy making strategies now, we'd deserve to perish."

It meant that they already had plans prepared for major risks, so there wasn't much to adjust.

This was the strength of a long-prosperous family.

"Then why are you all gathered here?"

"If the elders of the family were to play around like idlers, the children would become lax and unable to focus. Shouldn't we be serious first for those below us to follow suit?"

"Ah…"

"However, since Ah'er's friend can't be called an outsider to the Tang Clan, shouldn't she know the strategy?"

"Of course, she shared a bed with Ah'er after all."

"We can't help it if it's Ah'er's friend."

"Our Ah'er finally has a friend…"

"No, what are you saying?!"

Tang Lan-ah's face turned bright red.

Seeing this, Qing knew at least one thing.

\textit{This kid really doesn't have friends, huh.}

\textit{Would it count as Righteous Karma to be a friend to someone without friends?}

\textit{How bad must it be for the family elders to watch me with eyes that almost seem like looking at a daughter?}

"Ahem, ahem. Elders, that's enough."

Tang Clan Lord Tang Touzhong lightly summarized the situation.

"First of all, the Tang Center is basically a death trap. Without preparation, one can't enter and leave alive. Didn't Ah'er warn you not to step into the flower beds?"

"Yes. She said there were all kinds of traps laid out…"

The Tang Clan had an unnecessary number of flower beds.

Not only in front of and behind walls, but wherever there was even a little space, they had created flower beds surrounded by large stones.

In peacetime, they were used to grow poisonous plants or raise venomous creatures, and in wartime, they were used to immediately spread caltrops to stop enemies.

"We've delivered defense plans to the guest quarters for the other guests, but you are also a proper member of the Orthodox Wulin. Moreover, as my daughter's friend, you can't be called an outsider. So, will you face the enemy together with our family?"

"Yes. That's why I stayed."

At this, Tang Touzhong's eyes moistened.

"To think Ah'er has made such a good friend…"

It was the incomprehensible sensitivity of a middle-aged person.

"The Tang Center is an impregnable fortress. If it weren't for artillery, that is. So if we can just remove the artillery, we should be able to face even an army of ten thousand."

The Tang Center, with its poisons and Formations, prided itself on being the most dangerous place in Zhongyuan.

Moreover, how terrifying the Tang Clan's poisons were hadn't been properly revealed since the time of the Celestial Martial Emperor.

The main reason the Tang Clan focused on Medical Arts was also because they judged that it was difficult to develop further with poisons.

The problem was artillery.

One had to at least enter the Tang Center in order to be stabbed, made to drink, or poisoned in other ways.

If they just fired artillery from afar and turned the place into a wasteland of ruins, there was no chance to use Formations or poisons or anything.

"So once we remove the artillery, we win. Therefore, we must endure with minimal conflict until we can pinpoint their locations."

So the battle would start with a war of words.

The Sichuan Tang Clan was a member of the Orthodox Wulin.

Moreover, they provided free medical treatment and were one of the few groups that developed and improved agricultural pesticides.

The increase in crop and fruit production due to pesticides was said to be a turning point in agriculture before nitrogen fertilizers.

In fact, the Tang Clan's high Righteous Karma stemmed from this.

Of course, this was a fact known to no one.

However, with free medical treatment and cheap pesticides, it wasn't easy for the Imperial Family to suddenly attack the Tang Clan, which enjoyed robust public support.

If they made a mistake, not only would the Orthodox Wulin rise like a swarm of bees, but if civilians who sympathized with them appeared as well, there was no guarantee that the Tang Rebellion wouldn't appear following the Yellow Turban and Red Turban Rebellions.

The main reason was that the current government had lost public support by doing nothing but taking without giving.

So the Imperial Censor would try to find as many faults as possible before attacking to pin a definite charge of treason.

"So what we need to do for the time being is… Ahem."

Tang Touzhong coughed awkwardly.

"What is it?"

"…To endure without giving any pretext."

The plan was to continue the standoff as much as possible while identifying the locations of the artillery, then immediately remove the artillery when the battle starts and lure in the enemy to annihilate them.

However, the process of enduring would involve no small amount of humiliation.

They were in a situation where they couldn't make the first move against those who came looking for trouble on purpose.

Otherwise, they would have to answer for treason with immense compensation.

As in the Romance of the Three Kingdoms, for the people of Zhongyuan, justification was face, face was their honor, and honor was as important as life itself.

If one drew their sword suddenly saying they wanted to beat the shit out of someone, they would soon be treated as Public Enemy No. 1 of Wulin, so one had to fight appropriately while watching for others' reactions.

Although Wulin was essentially just a group of thugs, it was also almost the only safety device that allowed history to continue without major conflicts.

Of course, there were some who wanted to fight right away.

The Demonic Cult bastards who invaded when the time came were like that.

Still, the Demonic Cult wasn't completely without justification.

Ancestral revenge was a well-received justification since ancient times.

Rather than them, the Blood Cult bastards were the worst.

As a group that gathered all the world's scum like madmen, sexual deviants, drug addicts, cannibals, and so on, all they wanted to do was dye the world red with blood, thus causing Blood Disasters. As such, whenever they ran rampant, it became a complete mess.

However, the government couldn't be like that.

Another word for justification was legitimacy.

The government's weakness was always legitimacy.

After all, there was a history of the continent being divided, such as the Rebellion of the Eight Kings and the Sixteen Kingdoms of the Five Barbarians, when people rose up saying they should overthrow the imperial dynasty.

After hearing the situation, Qing thought.

\textit{Ah. So Wulin wasn't just about 'Let's attac! Let's protec!' and fighting life-and-death battles.}

\textit{There are unexpectedly complicated aspects, huh.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's Righteous Karma score had now exceeded 3,000 Points.

The 1,000 Righteous Karma Points received as a reward for overcoming the First Crisis were instrumental in this amazing rise.

It was Righteous Karma given with the Mission Window making a huge fuss about how it was the Path of Harmony, the Greatest Hidden Achievement, and whatever.

One could say it was worth overcoming a Crisis.

So that meant three martial arts.

Qing took time to seriously consider again.

This was no time to be stingy with Righteous Karma exchanges when facing a potentially decisive battle.

First, the Yijin Cleansing Method. Isn't it a bit useless?

It was a martial art with great efficacy in building muscles and strengthening the dantian and meridians.

However, her physical abilities had already transcended human limits, and her dantian and meridians weren't just strong but completely invincible, remaining fine even with all sorts of Inner Qi flowing through them.

Learning it would only give her something to boast about to her Master.

Then, is there a need to learn a martial art that wouldn't have much effect…

\textit{Wait!}

\textit{Master would like it, so how could I not learn this?}

\textit{I have three martial arts to exchange, so let's count one as filial piety.}

Qing immediately exchanged it, afraid she might regret it later.

With the feeling of her brain turning inside out, she unintentionally imitated a mute that lost their mind, gagging and retching.

The Daoism faction within her dantian cheered again.

As the Great Meditation Art happily extended a hand shape often adopted by the Buddha, the Yijin Cleansing Method also raised a hand in the same shape, and they high-fived each other.

"Ughhhh…"

Meanwhile, Qing just lay there for a while since her brain felt murky.