\chapter{Tang Clan's Paper Flower (14)}

At Poison Grandfather's praise, Qing proudly puffed out her chest and was about to answer confidently-

"Ow, ouch, sseeeup."

But feeling pain, she just answered while shrinking back.

"You don't need to be so surprised. I'm always excellent."

If you don't call an excellent person excellent, that of itself becomes a lie.

Therefore, even modesty could be rude for Qing, a genius talent gifted by the heavens, who couldn't bring herself to lie to an elder and simply stated the facts plainly.

"Yes, it's good to see you have such confidence. A martial artist should have such ambition!"

The Grand Clan Lord who accepted this could also be said to have issues.

"But, about that fellow's arm…"

"Ah. So that's why you came. How far did you look int- Euahhh, I mean, did you look into it?"

As she spoke, she realized she was saying something only subhuman vermin would say, so Qing quickly corrected herself.

The Grand Clan Lord, unaware of the circumstances, just blinked a couple times before answering, seemingly thinking nothing of it.

"It seems he was likely a Reinforced Blood Demonic Human."

"A Reinforced Blood Demonic Human!"

Qing shouted in surprise.

\textit{A Reinforced Blood Demonic Human!}

\textit{What on earth is that supposed to be!}

She shouted once, riding the mood that seemed like she should shout.

Even though shouting didn't suddenly make the unknown facts enter her head.

Qing, who didn't hold back when curious, asked.

"What's a Reinforced Blood Demonic Human?"

"Hmm, It is a kind of extremely vicious, how should I put it, um, yes, created by the Blood Cult's Dark Blood Supreme Law, um. Its characteristic is a body as hard as the Sword and Dao Invulnerability."

"The Blood Cult?"

"Yes. For an Embroidered Uniform Guard to have received the Blood Cult's Supreme Law, I think this is no ordinary matter."

In Jianghu, anything related to the Blood Cult could be said to be entirely evil without exception.

Because it was true.

It wasn't prejudice; the methods used by the Blood Cult basically always required blood.

The Dark Blood Supreme Law was the same, absorbing specially treated human blood into the target's body to create a Reinforced Blood Demonic Human with a body possessing Sword and Dao Invulnerability.

The Grand Clan Lord knew nothing about the special treatment in question.

Because he wasn't a member of the Blood Cult.

At any rate, it was a Supreme Law that absorbed other people's blood, so it was very evil and more than enough to be treated as a Public Enemy of Wulin.

"Hm? Isn't that a Living Jiangshi?"

"It's different from a Jiangshi. Even a Living Jiangshi only has consciousness alive, with the vitality in its dantian dead, so it just moves by consuming the remaining Innate True Qi."

"Oh. So the difference is whether they can use their own Inner Qi or not, right?"

"That's right. You are quite clever."

"Hehe. No no. I'm not. You flatter me."

Qing knew herself well, and knew that while she was always excellent, she was a bit far from being clever.

So this time, it was modesty.

"Then, does a Reinforced Blood Demonic Human unconditionally have forward compatibi- does this saying exist in Zhongyuan? Anyway, if you're going to make something, isn't it better to make a Reinforced Blood Demonic Human?"

"Reinforced Blood Demonic Humans are just tough, but their disadvantages are so great that even those Blood Cult bastards don't use them often."

"What are the disadvantages?"

"In exchange for having a body with Sword and Dao Invulnerability, they become dull. Their movements slow down by at least twice, and their joints and tendons stiffen, losing all flexibility, so their limb movements become stiff and linear. You fought one, so don't you know?"

"Ah."

Qing's expression turned very sour.

\textit{What? That was already more than twice as slow?}

That one move that cut her chest, even though she noticed it with her killing intent, she was too late to dodge and her breast was split in half like a mackerel being chopped.

She could empathize with the part about lacking flexibility and being stiff with linear movements.

Especially after Zhao Guo lost his reason.

Qing protested in indignation.

"For something like that, didn't he fight pretty well?"

"Fight well? His swordsmanship itself was overwhelmed by you, and he kept rolling around like a donkey. I thought Zhao Guo was just an idiot who had only trained in seclusion with no experience in Jianghu and couldn't keep up with you. Like those high-level Masters who struggle in actual combat after being stuck training in deep mountains."

"Hmm. Should I not brag then…"

Qing seriously pondered.

\textit{Still, if attacks can land, wouldn't it be possible to face even if the enemy becomes twice as fast?}

\textit{If you can block once with your arm and then stab…}

\textit{But if you fail, you'd really be split in half.}

\textit{Hm? No, wait.}

\textit{I was invincible with my shield known as Master.}

\textit{Come to think of it, if Zhao Guo hadn't been a Reinforced Blood Demonic Human, I would have beaten him to death long ago without my chest becoming three pieces.}

\textit{Thinking about it, it's unfair.}

\textit{If I had known he was a bastard who used other people's blood to become tough, I should have torn off all his remaining limbs too.}

\textit{He was truly the biggest son of a bitch under the heavens.}

"For an Embroidered Uniform Guard, and one of Guard Assistant Commander rank at that, to be a Reinforced Blood Demonic Human, this is no ordinary matter. We must immediately inform the Alliance and investigate. Your merit in finding evidence by tearing off an arm is beyond words. You did very well. Actually, while looking at it, I thought it was a strange sight, but this old man was wrong and you were right."

It was truly a bizarre thing to say in the world.

It was praise for tearing off an arm well.

However, given the nature of the matter, it was something anyone would nod and agree with.

"Grandfather, our Qing'er needs to rest."

At that moment, Tang Lan-ah interrupted the conversation.

Autumn was now in its latter half, and the nights were long.

As is common in primitive ancient uncivilized societies, when nights are long, one should sleep more.

"Ah. That is right. I am being thoughtless too. To think I would keep a sick child up. Yes. Rest well. In this situation, even the government will no longer be concerned about treason, so they shall withdraw soon. It is all over now, so you can rest easy and recuperate."

"Oooh."

That was welcome news.

\textit{If it's all over, then I can stop by the Emei Sect and go back…}

\textit{No, wait. I should go after my chest is fully healed.}

\textit{She said there won't be any scars.}

\textit{I'll send a letter saying I'll stay a bit longer before going.}

\textit{I don't want to worry them unnecessarily.}

\textit{How upset would they be if I showed up with bandages wrapped all around?}

\textit{Rather than that, it's better to become a runaway disciple and face nuclear retaliation later.}

\textit{If someone has to be in pain, it should be me.}

Qing decided to stay at the Tang Clan until she was fully healed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing stared blankly at the screen.

\begin{quote}
⧓□⧓□

30 60 90 120
\end{quote}

And she thought.

\textit{Wow. I'm really fucking awesome. It's a perfect score.}

Qing scratched her strangely itchy chest vigorously as she looked up at that beautiful score.

That's when it happened.

Someone hugged her waist tightly and whispered in a soft voice.

"Hoho, darling. Are you nervous because it's perfect?"

"Huh? No, no way. How could this man, Ximen Qing, be nervous?"

"Is that so? Then shouldn't you show me your gallant side?"

"Uh. Yeah…"

She's a beauty that looks familiar, but…

\textit{Who is she to call me darling?}

Qing tilted her head, but the question was only momentary.

For some reason, it just felt natural, as if that's how it should be.

At that moment, the pins came down from the end of the lane and neatly aligned themselves.

Qing tilted her head again.

\textit{Huh? Was the headpin, Pin No. 1, always shaped like that?}

It was a triangular pyramid with a wide base, somewhat translucent and even emitting a soft glow.

\textit{Wouldn't it not fall over with such a wide base?}

Qing had such doubts, but they too were instantly forgotten and accepted as natural, as if that's just how it was.

More than that, her chest was itching like crazy.

Qing scratched her chest irritably, and then the outer part of her thigh just above her knee started to itch too. Ah, damn it.

Finally, Qing frowned and gave up, inserting her fingers into the 15-pound house ball.

She lifted the ball high, stood with her feet together in front of the lane.

She pushed the heavy house ball with a slight rebound, then dropped it in time with gravity: one step, two steps, three steps.

And just as it was about to touch the ground, at a height of almost a paper's thickness, her thumb came out first, followed by her index and middle fingers twisting out of the holes a beat later.

The house ball, which had been drifting to the right side of the lane, rotated elegantly and then struck the side of the frontmost headpin at a 42-degree angle, pushing through.

At that, the triangular pyramid-shaped Pin No,. 1 shattered into pieces and screamed.

It was a strange yet desperate scream, saying "Aaagh ack ack aaaagh just kill me why do you torment me even in dreams you crazy Killing Star aaagh."

It was a scream so filled with terrible pain that even Qing, who was listening, felt hurt.

And then the remaining pins collapsed and were swept away with a refreshing Papapang sound.

\textit{Wow. Strike!}

That's when it happened.

A semi-transparent window appeared in front of Qing's eyes, and text floated on it.

\begin{quote}
[Omen, (Unknown)th Crisis]

Description:[You are under attack by Imperial troops.]
\medskip

Actions for Mission Completion

Righteous Karma) Help the Tang Clan defeat the Imperial troops

Evil Karma) Help the Imperial troops annihilate the Tang Clan

Heavenly Slaughtering Star) Kill everyone

[This choice could influence everything below Heaven.]
\end{quote}

Qing dismissed the Mission Window with disgust.

And then she realized.

\textit{Ah. This is a dream.}

"Sigh."

Qing let out a long sigh and thought.

\textit{This motherfucking Mission Window, I thought it was strange that I haven't seen it in a while. Is it seriously even showing up in my dreams now to cause trouble?}

Qing sat down on a chair and spoke.

"Yuanling, get out. If you don't want to die."

"Thanks."

Yun Yuanling, whom she hadn't seen in a long time, answered in a somewhat husky voice and walked away, her heels clicking.

\textit{Wait, who wears heels to a bowling alley?}

\textit{What an uncultured woman.}

Of course, Yun Yuanling was not at fault.

Originally, a shitty dream was disorganized; that was why it was called a shitty dream.

And Qing was invincible right now.

Because she was aware that the dream was a dream.

It was called a lucid dream.

However, the Heavenly Demon Spirit was not a made-up character within the dream.

Judging by the scream she heard earlier, it seemed Qing had been unknowingly tormenting it in her dreams every day.

\textit{It seems that punk, the Heavenly Demon, has been tortured in dreams every day.}

\textit{But I don't particularly pity it.}

\textit{How many lives has that mental parasite made miserable?}

From the Demonic Cult members of the past to the present, to all the victims devastated by the Great War Between Orthodox and Demonic.

It sacrificed all those lives just to fulfill its own grudge. It was a real son of a bitch.

Even if Qing had unknowingly tormented it every day in her subconscious, well.

It was something that could certainly happen, so she didn't feel any particular emotion about it.

\textit{More than that, look at this piece of shit Mission Window, barging into other people's dreams…}

\textit{Shit, and it's itchy.}

\textit{Is it where I'm hurt? No?}

\textit{The injured part is on the opposite side, though?}

That's when it happened.

The Mission Window that she had dismissed earlier reappeared, this time displaying only a part of the text she had seen before, enlarged.

\begin{quote}
[You are under attack by Imperial troops.]

[You are under attack by Imperial troops.]

[You are under attack by Imperial troops.]

[You are under attack by Imperial troops.]
\end{quote}

"Shit, I got it, so stop- Huh? Attack?"

In that instant, as her mind suddenly cleared, the dream collapsed with a crash along with a distant and dizzying distortion.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Gasp."

Qing opened her eyes wide, exhaling her remaining breath.

Then someone who wasn't Qing also made a sound of exhaling their remaining breath.

"Gasp."

For some reason, as soon as she opened her eyes, her gaze met directly with Tang Lan-ah's.

\textit{Well, she would be here since she said she'd take care of the patient and slept in the same bed, but hadn't she slept at all?}

Of course, that wasn't the important part.

Because behind Tang Lan-ah's tiny head, the uninvited Mission Window was still causing a commotion.

\begin{quote}
	[You are under attack by Imperial troops.]
\end{quote}

Qing's expression naturally hardened.

Then Tang Lan-ah, turning bright red even in the darkness, spoke flusteredly.

"No, it's not! It's a misunderstanding! So, uh, um, that, other, uh, palpation. That's right! It was palpation! Because you were going through palpation, I was just checking! There's no other meaning, it's palpation! Palpation! Isn't it suspicious! It's palpation! You might have internal bruising even if the outside looks fine!"

"What are you talking about? More importantly, are enemies-"

At that moment.

Boom……!

Along with a dull but massive explosion sound, an earthquake-like tremor traveled up through the floor as vibrations.

Creeeeak, the sound of wood twisting loudly, and dust from above the rafters fell like clumsy first snow.

"Huh?"

"What-"

And then, CRASH!!!

Something broke through the wall and struck a pillar, immediately shattering it.

Its pieces flew in all directions like a storm.