\chapter{Tang Clan's Paper Flower (13)}

The brightness returned to Qing's eyes.

As the Great Meditation Qi and Cleansing Qi chanted Buddhist texts together harmoniously along the Governing Vessel behind the spine, the malevolent star that had inserted a straw into the half-open Upper Dantian quietly slipped out and pretended it was never there.

The reason for its docile retreat was unknown.

After all, how could humans understand the intentions of stars?

Qing, now back to normal - or more precisely, returned to her emotional, stupid state full of random thoughts that were not particularly kind even after the Heavenly Slaughtering Star's killing intent had left her - looked down at the fallen Zhao Guo.

He was rolling his eyes, convulsing, and continuously foaming at the mouth with fine bubbles.

\textit{Wow. He's still not dead.}

\textit{No, wait. Maybe it wasn't enough to kill him?}

\textit{He just had his dantian pierced and the lower part of his pelvis shattered into thousands of small pieces.}

\textit{It wasn't an immediately fatal wound that would take his breath away.}

Qing squatted down, firmly grasped Zhao Guo's right wrist and elbow, and bent the joint in the opposite direction.

It was Qing's monstrous strength that could easily bend even steel.

Nevertheless, her hands just trembled as she held onto the fully extended arm.

\textit{What kind of body was this, for heaven's sake?}

As she struggled like that, Pop, Pop Pop Pop.

Along with the sweet sensation of tissue firmly attached to bone being torn away strand by strand, finally, Crack!

"Oooh. Finally. It worked."

Qing smiled gleefully as she repeatedly bent and stretched Zhao Guo's forearm in all directions.

Only then did the spectators realize Qing's intention.

They thought she was taking his pulse when she grabbed his wrist and trembled, but that wasn't it.

She was tearing off a person's arm!

The Imperial Censor shouted in shock.

"W-What are you doing!"

"Uh… Searching for spoils?"

"Stop this at once! How dare you, to an Imperial official-"

"A TRAITOR!!! An official? What do you mean an official? Didn't you all hear him insulting the Princess? Wow. It was really too much. How could he say such things to a woman? Even I felt humiliated listening to it."

She said this while twisting the skin and tendons of the forearm she had just torn off, spinning it around.

"AH!! RIGHT!! Don't tell me the Imperial Censor is on the same side as this traitor!! Is that why you're trying to protect him?!"

"No, no, no! It's not! It is not that! I am not!"

The Imperial Censor hurriedly and vehemently denied it.

Regardless of the Tang Clan, if he got wrongly involved here, he would have to be prepared for his entire family to be exterminated.

It was a petty and vile trick.

Perhaps, being the Tang Clan, they must have some poison that makes people see hallucinations.

Princess Xialian was the beauty of the era whom the Emperor himself had declared the Most Beautiful Woman Under Heaven, so it was actually natural for Zhao Guo to have seen an illusion of the Princess and dreamed of lewd acts.

As an Embroidered Uniform Guard who trained and resided in the palace, there wasn't a single guard who hadn't suffered from lovesickness.

However, Princess Xialian was the Emperor's most beloved daughter.

And some high-ranking officials like the Imperial Censor were particularly better aware than others of how extreme the Emperor's love for his daughter was.

He still cared for his grown daughter as if she were a child, even worrying about her sleeping comfortably and having her sleep next to him.

It was a secret of secrets known only to the highest officials in the Imperial Palace.

Insulting such a princess meant the annihilation of one's entire family was certain, and one would have to beg for mercy to see if it would be three generations or nine generations that would be affected.

Meanwhile, Qing finally saw results.

The stretched and torn area that was originally the right elbow was now mangled and bleeding profusely, and finally, with a Rip.

Qing, who had finally separated Zhao Guo's forearm from his body, stood up with satisfaction.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Although there had been an unsavory process-

To be precise, it was a life-or-death duel where not a single aspect wasn't unsavory.

But even if one took away that terrifying Hell Mouth Technique and the suspicious, cowardly suspected poisoning, what of it?

The fact remained that an Unrestrained Realm Master, and the third rank of the Embroidered Uniform Guards at that, had been toyed with and rolled around by a young girl of the mere Peak Realm.

The Imperial Censor had no choice but to retreat with the armless Guard Assistant Commander.

There was nothing more he could do by staying.

Moreover, the army's morale had hit rock bottom and was practically burrowing into the ground, so he had to deal with that as well.

Qing casually held out the forearm to Poison Grandfather like a gift.

"Grandfather, this was strange. Can you take a look? It doesn't seem like a human body. I mean, steel- no, not even Ten Thousand Year Cold Iron should be this hard."

There was no reason to tear off and bring a person's arm if you weren't going to roast it or make soup with it.

She brought it because it was strange and wanted him to examine it.

Of course, that was limited to the fact that she brought it.

If Qing hadn't been satisfied with the castration, it wouldn't have been strange if she had torn it off for fun and thrown it away.

"What do you mean?"

Just as the Grand Clan Lord was about to ask what on earth she meant by such bizarre words after receiving it…

"Hey!! What are you even doing! Your appearance is…! I'm really upset!"

Tang Lan-ah shouted and grabbed Qing's hand, dragging her away.

In fact, none of Qing's wounds were serious enough to be life-threatening.

In truth, if bones were damaged or muscles were cut, she wouldn't be able to use her strength at all, Heavenly Slaughter or not.

If she had been cut in an area with heavy bleeding, she would have fainted and collapsed midway.

At most, they were just minor cuts on the skin.

However, the wound on her chest was quite deep.

Qing, led by Tang Lan-ah into the medicine hall, finally took in the wound on her chest.

"Wow. My chest has become one and two halves. Ugh, so gross."

1 + (1/2) × 2. It was a rather accurate expression.

Since no part had fallen off, the total amount was the same, but the left breast had been diagonally cut vertically, revealing a gross cross-section that was kinda like, like… Like you know?

"Is this the time to say such things!"

Tang Lan-ah slapped Qing's shoulder and exhaled rapid, angry breaths.

"If it had been just a little deeper, all your ribs would have been cut off! Why weren't you more careful!"

"No, against an Unrestrained Realm, this much is pretty goo- Nevermind. I am sorry…"

Qing immediately retracted her words upon seeing Tang Lan-ah's expression with tears welling up.

She wasn't cruel(?) enough to upset someone who was worried sick.

Instead, Qing tried to subtly change the subject.

"Um, do you think it will leave a scar?"

"You worry about scars yet you don't even take care of your body!"

"No, that's not it. Wouldn't a scar look kind of cool? Usually-"

"Hey!!!"

Slap. Qing ended up getting hit once more.

It was only a slap because it was Tang Lan-ah.

If Ximen Surin had heard this, it would have been a yap of fear that would have called down a profound strike from a Master who had reached the Profound Realm, regardless of injuries.

"I'll take responsibility and make sure no scar remains, so don't say such useless things."

Qing felt a little wronged.

It was split diagonally vertically, and then cut horizontally about two finger joints.

Combined, they made a perfect cross shape.

Shouldn't a Sword Master have at least one such scar?

"No, really. It's okay if it leaves a scar, so don't get so worked up."

However, Qing's sincerity didn't get through.

Far from getting through, it only invited a huge misunderstanding.

Even if a woman didn't mention her breasts out loud, was there anyone who didn't care about them?

Whether they were small, large, or just right, they were precious things that one would secretly look at alone, worrying if the shape was okay, if the color was strange, if they were pretty or not, or what if people said something later.

If someone said that it would be cool if a scar remained after it had been split in half, as if worried that the counterpart would feel sorry, how could one not feel even more sorry?

In truth, Qing had said something that could be misunderstood.

What use would a cool scar on a woman's chest be?

It's not like you'd show your chest to passersby and say, ‘Look at this. Wow, a sword scar! So you know about the cross, huh?' and brag about it.

"You really… Really… Hic."

Tang Lan-ah finally burst into tears.

And then, she had to pay dearly for toying with a woman's pure heart with nonsense.

"Ack! It hurts! Just a little gentler! Help, kyaak! Someone help! The physician is trying to kill me!"

"What? What are you saying? I used plenty of anesthetic powder, so why are you exaggerating? This much would work even on an elephant."

"Uh, that, opium… Can't you give me some opium?"

"You, do you know how harmful opium is?"

"Sss, hoo, hoo. Sniff, sniff. Ack!"

For the first time since her journey into Wulin, Qing cursed the Strategy Guide.

\textit{Are you for real? Shouldn't anesthesia at least work?}

Why does opium work but anesthesia doesn't?

In fact, pain itself was necessary for the body's survival.

Therefore, anesthesia was harmful.

Opium didn't eliminate pain, it just elevated the mood to mask it, so in modern terms, one could make an analysis about something endorphins something or whatnot. However…

Qing doesn't know anyway.

So all she could do was curse her cursed Constitution that didn't even respond to anesthesia and the person who recommended that choice.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was that night when Poison Grandfather came to visit.

Qing happily welcomed the Poison Elder who had generously given her poisons.

"Wow. That poison was incredibly effective."

Of course it would be effective.

In the Tang Clan, there existed seven supreme poisons called the Seven Great Extreme Poisons, which were considered almost products of chance even in the history of the Tang Clan.

They were the Eight-Colored Powder Poison Pill, Soul-Dragging Water, Immortal Waste, Soul-Seizing Oblivion, Seven Steps Soul-Severing Powder, Five Poison Divine Dance, and Soul-Destroying Pill.

The ingredients that the Grand Clan Lord had personally modified were these supreme poisons of the Tang Clan.

Moreover, the Grand Clan Lord was the Greatest Poison Master Under Heaven.

It was the result of the world's most vicious poisons being modified by the world's greatest craftsman.

Even masters above the Profound Realm, let alone the Unrestrained Realm, would have ended up in a miserable state if they couldn't quickly capture and expel or burn off the Poison Qi in the early stages.

Moreover, Zhao Guo had all but lost his reason and didn't notice the Poison Qi, and this was combined with the fact that his meridians had already been greatly damaged by the White Hand Demonic Arts.

"Do you have any more? I used all three pills…"

"Hoho, it was something that came out by chance, so that was all I had. I was actually going to ask if you had any left. It can't be helped, it seems."

The Grand Clan Lord also showed signs of regret.

He had many such works as he made them as a hobby.

However, there was no one to use them on, so he left them unused and didn't write down the formulation separately.

But after seeing the terrifying effects of the modified Soul-Seizing Oblivion, he thought he should properly name it and add it to the clan's list of Extreme Poisons, but now he was told it had all been used up.

"Ah. That's right. By the way, how did you administer the poison? Did you learn some separate Poison Utilization Techniques?"

"Oh. That."

Qing held out her hand, and Cui Liweng stared blankly.

Only after Qing pursed her lips and whistled did he realize her meaning and take out Fushen-di to hand it over.

Qing, who received Fushen-di, mimicked putting a poison pill into the flute hole and then shook it once with precision.

If there had been something inside, it would have bounced out due to centrifugal force.

Fushen-di was a truly versatile club that could withstand Force, make sounds, and even fire poison pills!

"Oho! Child, your ingenuity is truly admirable!"

The Grand Clan Lord didn't hold back his admiration at this.
