\chapter{Tang Clan's Paper Flower (3)}

The martial artists of Wulin rarely fell ill.

This was because both the External and Internal Arts fundamentally had the function of boosting health.

Qing had never even caught a cold while spending winter with just a single layer of thin, see-through cloth, so minor illnesses were not enough to invade a martial artist's body.

Even if not martial artists, compared to Qing's homeland, the people of Zhongyuan were unreasonably robust.

So the news that Ziyou had fallen ill gave Qing a somewhat strange feeling.

They said he was weak, and it turned out to be true.

As expected, one shouldn't underestimate the insight of a doctor of traditional medicine.

Still, one should visit a sick friend.

As a guest, she didn't have much to do anyway.

Originally, when a friend was sick, one should at least send a message to inquire about their well-being.

Humans are creatures that become sensitive when sick, so when ill, they can turn resentment into retribution.

So when Qing saw Ziyou, his complexion was indeed pale, but… \textit{Hmm? Wasn't his complexion always pale?}

"W-What brings you here?"

"What do you mean? I heard you were sick, so I came to see you. Are you feeling better? Let me see, do you have a fever?"

Qing placed her palm on Ziyou's forehead.

In fact, the method of putting a palm on the forehead was practically meaningless.

Qing's hands were always cold due to the effects of the White Hand Demonic Arts, so whether it was the forehead or anywhere else she touched, it would feel warm and seem like there was a fever.

However, for Ziyou, it was a shocking act.

From the moment she came to visit, it didn't fit with Zhongyuan where the differentiation between men and women were supposed to be quite separate, and now she even placed her hand on his forehead.

Perhaps because of the cool touch, he felt heat rapidly rising to his face.

"Oooh. It's quite hot, huh? Your face is red too."

"No, that's…"

Ziyou, who was actually just pretending to be sick, couldn't find words to continue.

Originally in Zhongyuan, the excuse of being bedridden was an almost invincible trump card that meant 'I'm not receiving guests.'

The Tang Clan was essentially a collection of physicians, and they had focused on medical arts since the time of the Celestial Martial Emperor.

As they were practically the best medical family in Zhongyuan, wouldn't the Tang Clan have at least taken a pulse for a guest?

As such, there was an unspoken agreement of 'Ah, this bastard is faking it, but since he claims to be sick, let's just say he has a cold.'

"Come on, how can a man be this weak? You seemed to come from a well-off family, couldn't you just pick up and learn some martial arts?"

"Well. Um."

But Qing had always strayed far from common sense.

Qing's expressions were inherently honest.

The concern clearly reflected in those large eyes left Ziyou speechless.

He thought that no precious gem in the world, said to be more sparkling than anything, could compare to those eyes.

"What? Why?"

"No, it's nothing."

Ziyou, who suddenly came to his senses, glanced at Cui Liweng.

'Hey, didn't you teach her common sense? You must have known it was fake, right?' was what his look said.

Cui Liweng just snorted.

'Should I tell the child who's worrying that he's just faking it and there's no need to care? You rascal. Minus twenty points.'

Ziyou had suddenly fallen from the lead in the competition.

Though of course, what use was there in Cui Liweng giving points anyway?

Ziyou suddenly had a thought and hurriedly asked.

"Wait, is the Tang Clan not in quite an uproar right now? How come you have not left? Seeing as how they have been caught up in the treason."

Qing's hand lightly tapped Ziyou's crown.

"Your speech. Are you not even trying to change it since you're sick?"

"That's not important right now."

"No, what? Why are people like this? When they're guests eating for free and getting pocket money, it's all fine? But when help is actually needed, they change their faces and all run away?"

"No, but treason is…"

"I was originally planning to visit the Emei Sect, but this happened. It feels like I'd just be eating and running when needed. So I should at least help a bit."

Again, Ziyou glanced at Cui Liweng.

The look meant, 'She clearly doesn't understand the fear of treason, why didn't you tell her?'

Cui Liweng snorted again.

Cui Liweng had no particular reason to dissuade her.

Basically, Cui Liweng had an attitude of 'Do whatever you want.'

He knew that Qing was someone who took terribly good care of her life, and that staying to help didn't mean she was going to act like some suicide squad prepared for death.

Also, her Qinggong was so excellent that there were few in the world who could catch her if she ran away.

And as a high-ranking elder of Daoism backed by the Zenith Among Women, even the government couldn't push her too far.

And if all else failed, there was always the Divine Cult.

Above all, he couldn't bear to hear her resentment again for blocking her path.

Seeing that he had no intention of stopping her, Ziyou finally let out a big sigh and spoke.

"Haah. Look here, Friend."

"What?"

"This matter won't be easily resolved. The Imperial Family must have been waiting for this moment for a long time. Ever since that outrageous fellow called the Celestial Martial Emperor."

The shock the Imperial Family received after the Celestial Martial Emperor's attack on the imperial palace was truly earth-shattering and heaven-overturning.

Until then, martial artists were just local strongmen who could be pushed aside at any time.

They were one of the tools the Imperial Family used for governance.

The Zhongyuan were too vast for the Imperial Family's eyes to reach everywhere, so instead, they held the leash of the hunting dogs called Wulin.

However, the Celestial Martial Emperor proved that the martial prowess of a single person could indeed reach the heavens.

As such, he drastically undermined the authority of the Son of Heaven.

Even the Son of Heaven, who inherited the orthodox lineage entrusted by Heaven to rule, couldn't crumble mountains and split the earth while wielding only a single sword.

"So leave the Tang Clan now. Given the situation, the Tang Clan won't try to hold you back either."

"Why should I?"

"Didn't I say? It won't be easily resolved. If you get caught up in treason, even you won't be safe."

"Well, that's for me to handle. But isn't it funny? That's not the important thing right now, is it?"

"Then what on earth is more important?"

"We should first determine if the Tang Clan is really guilty. In my opinion, even if the Tang Clan isn't afraid of the Imperial Family, did they have any reason to assassinate the Grand Prince? Even I can tell something's off. Besides, they say the Tang Clan makes a lot of money selling poison, so that's not even evidence that the Tang Clan did it, right?"

Ziyou frowned.

It wasn't wrong, but it was words that didn't even show the minimum courtesy towards the Imperial Family.

"Well, is the Tang Clan truly innocent?"

"What? Did the Tang Clan really do it?"

Qing asked back in surprise.

If the Tang Clan really did it, that would be a different story.

Just as Qing's ears were about to perk up, Ziyou shook his head and answered.

"That's not what I mean. Are these groups of righteous experts called Wulin sects really innocent? Aren't they just swinging their swords, exploiting civilians, ignoring government rule, and doing as they please? What right do they have?"

"That's ridiculous. Then what right does the Emperor have to sit on his high seat and rule?"

"…?"

Ziyou's expression turned dumbfounded.

"I mean, isn't that the case? Are we supposed to shut up and follow, just because he was born as the Emperor's son? If both sides are going to intimidate and suppress with armies anyway, what's the difference between the Imperial Family and Wulin?"

"How can you say such things? The Son of Heaven is someone who Heaven has bestowed-"

"What bullshit are you spouting? Did the Emperor tear through the sky when he was born and shout that he alone is noble both in above and under the heavens?"

"No, what, how dare… blasphemy."

Ziyou couldn't continue his words properly.

It was an extreme statement for people of Zhongyuan.

'Is there anyone who is born to be a king, a duke, a general or a minister?'

This saying phrased as a rhetorical question, which meant that there was no special seed for kings and nobles, was an outrageous statement that only traitors to the world would dare utter.

"You shouldn't carelessly say such things."

"Did I say something wrong? From what I've seen, I don't know about other sects, but doesn't the Tang Clan have the qualifications to act like kings? They drive out Unorthodox Faction bastards and provide free medical care. I mean, just look at the Ouyangji incident this time."

"That's…"

"They spent gold, put bounties on Ouyangji, put counteragents in wells, did everything they could. Of course, in the end, it was resolved by my outstanding intellect, but isn't that originally what the Emperor should do?"

"…Ahem."

Ziyou, at a loss for words, just coughed unnecessarily.

Qing clicked her tongue at this.

"I guess they do say that only those who didn't benefit from their ancestors work hard at ancestral rites. Rather than praising an Emperor who hasn't done anything for you, wouldn't it be better to become a Wulin practitioner?"

"…Still, such words should be kept to oneself and not spoken in front of others. The mere act of uttering them could make one sound like a traitor."

"I have some tact, you know? Do you think I'd go around saying these things in front of others?"

Qing was saying this in front of the current Emperor's younger brother.

"Or are you going to report that your friend said something treasonous?"

"That's not it, but…"

"Then it's fine. Anyway, take care of yourself. I'm confident I can slip away if needed, so I don't mind. But you should avoid getting caught up in this unnecessarily. Just stay in bed sick."

After that, Qing chatted about trivial matters for a while before leaving.

In the room where Ziyou was left alone, three human shadows suddenly dropped from the ceiling.

"Isn't that thing really a traitor? I've never heard such terrible words in my life."

"Watch your words. How dare you call her a thing? That's the woman His Highness has taken a liking to."

"Ah, really! This mouth of mine again. Your Highness, please pretend you didn't hear that. This lowly one misspoke."

"No, no. Old Dog, stop with these groundless slanders. If it leaks out, wouldn't it block an innocent woman's marriage prospects?"

Ziyou hurriedly waved his hands.

At this, Old Dog smiled slyly.

Then another masked person spoke up.

"Even to this lowly woman, she seems like an excellent woman. After all, what's important in a relationship is the loyalty after it's formed. Isn't it admirable that she's willing not to avoid difficult times?"

"Didn't Hag Yan clearly fiddle with her throwing knives earlier? You were emitting killing intent from your eyes, and now you're changing your words, making me look like the strange one."

"I do not know what you're talking about. Your young eyes must be getting dim already, seeing things."

The masked person called Hag Yan\footnote{燕婆/ Yan Po, lit. 'Yan granny'. The 'Yan' character means 'swallow bird'. Yeon Pala (연 파라) in the original text} played dumb.

Ziyou frowned and stopped the chatter.

"That's enough. More importantly, did you find the rat?"

At this, the atmosphere among the three people turned ominous.

The one with the youngest voice answered.

"It was that bastard, the Rotting Flying Fox. How dare he forget the grace he received from Your Highness. We shouldn't have taken in that animal. He was wagging his tail so very hard for that eunuch from the Eastern Depot\footnote{Ming dynasty's secret police, named as such because its first office was located east of the imperial palace. It's run by eunuchs}."