\chapter{Tang Clan's Paper Flower (2)}

The woman pulled something out from her bosom.

She grabbed a long cylinder and aimed it at Tang Lan-ah, with a string attached to the back that she held with her other hand.

Qing didn't know what the object was.

But as someone from the modern world, she could immediately recognize that a long cylinder pointing at someone was extremely dangerous.

Qing was startled and pushed Tang Lan-ah while reaching out towards the cylinder.

However, Tang Lan-ah recognized what it was.

It was a type of hidden weapon called a Needle Tube.

It was a hidden weapon that used the tension of stretched leather or tendons to fire needles inside, usually not powerful enough to be considered lethal on its own.

The problem was that the needles were coated with poison.

As Tang Lan-ah rolled from her sitting position in a world that seemed to be turning, she saw Qing's back as she took a step forward, and a hand imbued with sunset-colored Qi extending through the gap below her surprisingly wide hips for her body type.

Tang Lan-ah screamed out.

"Run aw…!"

But it was too late.

THWACK!

The sound of strong tension striking leather.

At the same time, thousands of tiny objects reflected off the palm, sweeping the area in front of Qing like a storm.

In a world moving slowly due to momentary concentration, the short broken needles embedded themselves into the woman's body with a rapid pattering sound, her skin rippling as she was pushed back and floated into the air.

As time's flow returned to normal, the woman who had been flung away collided with the door frame and tumbled down.

Tang Lan-ah, who had rolled one and a half turns from her sitting position and sprung up, immediately grabbed Qing's wrist.

"Hey! You! What are you doing?! Do you even know what that was?!"

Then she pulled Qing's long hand in front of her face and started kneading it.

"It's okay. I deflected them."

"You idiot! What if even one needle had hit you?!"

Tang Lan-ah pulled Qing's palm close, almost burying her nose in it, rubbing and kneading while her eyes moved rapidly.

But the White Hand of the White Hand Demonic Arts wasn't soft enough to be pierced by mere needles.

"What the? Was she trying to die or something?"

The woman had something like cactus spines chaotically embedded all over her exposed skin and clothes.

Black, blue, and purple spots were rapidly spreading on her skin, and blood was flowing from her mouth, nose, and ears, while her eyes were still filled with blood, turning the whites red.

"Most Senior Brother, I'm sorry. I couldn't… avenge you…"

"Is that important right now?!"

Tang Lan-ah was busy examining Qing's palm, not even paying attention to the assassin.

As the assassin still glared at them with a resentful expression even in that state, Qing waved her free hand and smiled, seeing off the dying person.

"Kuhak!"

At this, the woman's eyes bulged, and she vomited blood before her eyes glazed over.

It was truly a fitting end for a high-spirited assassin.

In carrying out her mission, she clearly explained why the target had to die, which was a way of preaching that didn't withhold enlightenment, even to an enemy.

Moreover, even while dying after failing, she tried to kill the interferer by shooting glares until the end, showing an admirable professional spirit.

However, what she didn't know was that glares didn't have any oomph and couldn't kill people. This must be a lack of knowledge because the physics of Zhongyuan is still at a primitive level.

If she at least hadn't shouted 'Nemesis of the Most Senior Brother! DIE!', Tang Lan-ah, who was the target, wouldn't have been able to avoid the poisoned needles.

But it was something that those who say they will avenge their nemesis absolutely could not resist.

If one could give up the sentiment of 'Know why you're dying and regret it!', would they have come into the heart of enemy territory to shoot hidden weapons in the first place?

After meticulously examining the palm for even the slightest scratch as small as a hair, Tang Lan-ah finally let out a long sigh of relief.

Then she immediately shouted again.

"That was dangerous! Who in their right mind would block that with their hand, no matter how confident they are in their Hand Arts!"

"Uh. Me?"

"Is that supposed to be an answer?!"

Tang Lan-ah's tone was fierce.

So Qing decided not to mention the stinging in her side.

It seemed like something had leaked a bit, but since the poison wouldn't affect her anyway, she figured it was probably just some thorns stuck in her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There are mainly two ethnic groups living in Yunnan Province.

One was the Bai people, descendants of the former Dali Kingdom.

The name Bai came from the ethnic group's fanatical preference for the color white, with their clothes being white, nice houses being white, Buddhist temples being white, and even palaces being white.

They were evaluated as country bumpkins who preferred white over the auspicious purple, but at least they weren't treated as barbarians.

In addition, there was the pride, the self-esteem, and the honor of the Bai people. The Diancang Sect.

The Diancang Sect, which inherited the Daoist lineage while uniquely combining it with Dali Bai Buddhism, straddling both sides as half-Daoist and half-Buddhist, was one of the symbols of the Orthodox Wulin among the Nine Sects and One Union.

So it was the parents' ambition to send their Bai children to the Diancang Sect, whether they had talent or not.

Thanks to this, the Diancang Sect, which cherry-picked only the elite of an entire ethnic group as disciples, had a solid path laid out for its future prosperity.

And the other ethnic group was the Miao people.

It might have made Qing think "Could it be…?\footnote{Miao also used in Korean webtoon as noun for beastman}" if she had heard the name, but in reality, they were just an ethnic group with characteristics closer to Southeast Asian people.

The Miao were one of the representative despised barbarians, being short, with plump body shapes, and having skin that was either dark or yellow.

Surprisingly, they lived in humid jungles, and the Five Poison Sect and the Southern Barbaric Beast Palace were the sects of the Miao people.

Among these, the Southern Barbaric Beast Palace actually didn't care about the outside world at all.

They were busy frolicking with slightly fierce pets like tigers, bears, and leopards among themselves, not paying much attention outside the jungle.

It was also a sect frequently visited by animal lovers from Zhongyuan.

But the Five Poison Sect was different.

They were ridiculous people burning with a sense of mission to reclaim their ancestral lands, claiming that in ancient times, long long ago, the Miao people were the masters of Dongting Lake.

As such, until a month ago, Hu Zhenchi, the Sect Leader of the Five Poison Sect, was living each day with a heart full of thoughts about reclaiming their people's domain again.

If things went well, even if not as far as Dongting Lake, the Miao people could advance into Sichuan.

It was also an opportunity to quench the resentment of their ancestors by killing large numbers of those hateful descendants of invaders, the Han people5.

At any rate, Dongting Lake was a part of the Yangtze River.

Four of those Yangtze Rivers flowed through Sichuan, so their ancestors would probably accept that much.

And so, their disciples had gone out to carry out a great task.

But they came back utterly defeated.

The damage to the First-Grade Disciples was especially severe.

The Most Senior Brother of the First-Grade died, and the second, third, fifth, sixth, and ninth also died.

Moreover, there was no news of what happened to his daughter who had rushed out after hearing this ne-

"It is terrible! Xia'er, Xia'er has…"

"What about Xia'er! Where is she now?!"

"Well, that…"

And just now, Hu Zhenchi, the Sect Leader of the Five Poison Sect, learned news of his beloved daughter, the Fourth Disciple of the First-Grade.

It was the horrific news that she had failed in an assassination attempt in the heart of the Tang Clan and her naked corpse had been hung on the main street of Sichuan Province.

"These… these bastards! These wretches, who deserve to be pickled and made into wine! What wrong did Xia'er commit…! How, how could this…"

Attempting assassination was indeed a great wrong.

Of course(?), to a father who lost his daughter, it was a trivial matter.

A blue resentful poison gleamed in Hu Zhenchi's eyes.

"…Tell the Great One that if he can make it possible for me to brew wine with the heads of those Tang Clan bastards, I shall do anything in my power."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tang Clan Lord Tang Touzhong was also jumping up and down in fury.

His most precious daughter had been attacked in the heart of his noble clan.

Of course, by heavenly fortune, the clan's benefactor was with her, so it was passed without harm.

However, the assassin didn't even try to hide her identity and infiltrated the clan with the determination to die together, even disguising herself as a patient to attack the clinic.

It was a horrific atrocity that even the Demonic Cult wouldn't commit.

At the Tang Clan Elders' Conference, Tang Touzhong raised the agenda in a voice thick with the scent of blood.

"We can no longer tolerate this. We must eradicate the Five Poison Sect."

They had been indulgent until now, even if the other side unilaterally called them rivals.

After all, they were just country bumpkins eating poison in a corner of the jungle. If they had been closer, they would have been beaten long ago, but they were left alone because they were a bit far away.

The Tang Clan members who collected poison also knew well how treacherous the jungle could be.

However, the head of a family responsible for an entire clan should not rashly decide on a campaign based on personal emotions like revenge.

That was why the Tang Clan's oldest Elder, Grand Clan Lord Tang Caiyun\footnote{Dang Jae-un (당재운) in the original text}, opened his mouth.

Even the current Clan Lord couldn't help but listen to the opinion of the Grand Clan Lord, who had been silent to maintain the authority of the current Clan Lord.

"They dared to target Ah'er. Crush them thoroughly so that this never happens again."

However, the Grand Clan Lord's entire life in his old age was devoted to seeing his cute granddaughter's cutesy.

"That's right. It is already an unstable time, so it would be best to use all the Fire Bombs and blow them away completely. It is not good to keep them in storage at the current moment."

This was the opinion of the Chief Steward who managed all the clan's warehouses.

They had plenty from embezzling the saltpeter mines, and they had money to buy sulfur.

So why not make gunpowder?

If one didn't, he was not a true man and should have his little pepper removed immediately.

Because gunpowder was a substance that all men aspired to.

However, as the amount they had gradually made accumulated to quite a weight, it became awkward to keep.

It was an amount that couldn't be overlooked even by the paper tiger-like6 government offices.

Rather, it was an issue that would cause even more alarm because the government offices were growing gunpowder as a countermeasure against martial artists.

So the opinion was to blow up the Five Poison Sect while getting rid of the evidence at the same time.

"That's a good idea. Let's pour all the Zhemu powder and rot the land so they can never rebuild."

"Is rotting just the land enough? It should be an eye for an eye. Those Miao barbaric bastards dared to target the water source of Chengdu, so let us dump Immortal Roux into their water."

The high-ranking members of a noble clan were ultimately just a gathering of relatives.

And since they had touched the most beloved girl in the Tang Clan, there was no one to stop them; everyone was busy coming up with even more vicious methods.

As such, it was decided that they would poison and sweep away the entire city that served as the Five Poison Sect's foundation.

And so, the Tang Clan shook off its spirit to engrave its famous family motto in Zhongyuan once again after a long time.

Repay kindness twofold, and grudges tenfold.

However, unfortunately, that plan was thwarted.

It was because of an announcement borrowing the Imperial Edict of the Imperial Censor who had come down personally to investigate the death of an imperial family member.

 \begin{quote}
-Clear evidence has been secured that the Tang Clan's extreme poison was used in the assassination of Grand Prince Dexian.
 \end{quote}

Therefore, all those with the surname Tang in Sichuan are to face inspection as traitors.

Moreover, all doors to their family's traditions and secrets are to be opened wide to ensure nothing is hidden.