\chapter{Tang Clan's Paper Flower (12)}

Often, when people of Jianghu thought about the owner of the Heavenly Slaughtering Star, they imagined a crazed killer intoxicated with blood.

In fact, that wasn't entirely wrong.

But it wasn't quite the same; at least the Heavenly Slaughtering Stars didn't go berserk like mad dogs and bite to draw blood.

Even the image of a blood-crazed killer was actually an illusion deliberately adopted by past owners of Heavenly Slaughter.

Since the rarely appearing Heavenly Slaughters never met each other, it was just something individuals used as a method to conceal themselves.

Rather, the Heavenly Slaughtering Stars were closer to meticulous killing fiends.

Thanks to this, Qing's mind now sharpened clearly as she received the energy of Heavenly Slaughter.

Her first thought was a bitter reflection.

\textit{Why didn't I think it was strange?}

\textit{Is Force Armor some kind of absolute magic barrier?}

\textit{It's not some new superconducting shock-dispersing material, so how could it perfectly absorb all impacts?}

Qing, who understood superconductivity as something akin to 100\% perfect, thought like the social science major she was as she examined Zhao Guo.

\textit{The hell. It wasn't a matter of Sword Qi versus Force to begin with.}

\textit{If I hit him that much, even if it wasn't Zhao Guo but Zhao Guo's grandfather, some flesh should have burst, bruised, and bones should have at least cracked.}

Her eyes, which had lost their luster with an indifferent coldness, quietly reflected Zhao Guo's figure.

\textit{It seems like he's completely lost his reason.}

\textit{Well, that makes it easier, I guess.}

Keep the heart hot, but the head cold.

It was something all Masters in the world say at least once, but it was actually difficult for even themselves to maintain.

When you lose your reason and are caught up in killing intent, you become honest.

Your eyes only see the place to stab, and your body follows without deception, becoming a fool obsessed only with slaughtering the enemy.

Qing faced Zhao Guo with a much more relaxed mind.

The approaching sword tip wavered left and right, splitting into three forms, aiming for the neck and heart, with one curving diagonally towards the waist.

Stepping sideways, twisting her pelvis, and pulling her spine back, a fierce sword wind brushed past her neck, and then… Her chest stung!

\textit{Ack! Shit, I got cut again.}

Even then, one attack remained, and Qing's hand touched the side of the incoming blade, gently pushing to change its direction.

Zhao Guo's body swayed outward following the blade.

Qing stepped to the left while swinging Fushen-di, and the Ten Thousand Year Cold Iron club dug into the back of the knee, cutting through the air with a swish.

Thwack!

When you hit the back of the knee, the knee flies forward.

Zhao Guo collapsed into a kneeling position, then tumbled and rolled away.

Qing didn't follow, but quietly exhaled while her eyes tracked Zhao Guo's figure.

\textit{Even just now, the hit didn't land at all.}

\textit{Strange. Is it possible for impacts not to land at all?}

\textit{But would an Unrestrained Realm Master get hurt or break bones just from rolling a bit?}

After rolling around, he sprang up using the rebound and charged again, taking a fighting stance.

"I'll kill you! You bitch! I'll kill you!"

\textit{Hmph. You shouldn't be the one talking.}

Qing snorted and charged forward, kicking off the ground.

Because the opponent had lost his reason in anger, it actually became much easier to deal with him.

This was why Qing always ran her mouth, aiming for this.

Of course, it was also thanks to Qing's reason having cooled down.

But in her state of being unhinged by the Killing Star, she didn't feel strange because she considered herself normal.

She just thought that after continuously getting hit and being cut badly twice, she was now getting used to that sword technique as it became familiar.

Qing extended Fushen-di straight out, firmly striking Zhao Guo's blade guard.

The twisted force acting at the starting point of the sword path caused the technique to lose direction and waver, drifting off course.

Then, blocking the incoming claw attack with her forearm, \textit{Ack! Fuck! That stings!} She kicked his shin with all her might using her toes, causing Zhao Guo to lurch forward.

Fushen-di left an afterimage as it struck Bam! on the back of Zhao Guo's head.

Zhao Guo slid across the Tang Clan's front yard, drawing a long line with his face.

As Zhao Guo sprang up again, Qing continued her vicious scheming.

\textit{If I can tire him out like this, it should work.}

\textit{His Inner Qi isn't infinite, and how long can he keep spewing Force and maintaining Force Armor defense techniques like that?}

\textit{But what if he comes to his senses?}

\textit{If he says ‘Hoho, oopsie, I lost' and declares defeat before running away, can I chase him down and kill him?}

\textit{No, I won't be able to do that.}

\textit{What other means do I have?}

\textit{Buddha's Palm? That's too easy a death. Let's hold off on that for now.}

\textit{Black Slaying Demonic Palm? If even the White Hand Demonic Arts didn't work, then…}

\textit{Lustful Immortal Disrobing Dance? A guy whose out of his mind with anger probably won't go 'Hehehe' just because someone takes their clothes off.}

Qing checked what she had while extending Fushen-di towards the charging Zhao Guo again.

One Hundred And Eight Asura Sword, Heavenly Falcon Grab.

The end of Fushen-di, extending with the imagery of a falcon snatching a rabbit, pushed aside Zhao Guo's shoulder, twisting the starting point of the Demon-Conquering Sword and drawing a completely off-course sword path.

At that moment, she hooked her ankle around his and used the principle of the Antigravity Qinggong of the Yue Maiden Footwork to stomp the ground.

Zhao Guo flew off in a parabolic arc.

Even in the midst of this, the Killing Star, who hadn't stopped her thinking, suddenly stretched her mouth into a long grin.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Cui Liweng was about to spring into action the moment Qing's chest was badly cut.

However, he stopped after just taking the stance to deliver one Force Compression attack.

This was because the nature of the life-or-death duel had completely changed.

Only Tang Lan-ah, with her poor judgment, stamped her feet anxiously before clinging to the Grand Clan Lord.

"Eek, what should we, we, Grandfather, we need to help Qing'er."

"Let us wait and see for now. It does not seem to be a serious injury. Above all, hoh… I'd like to ask how the Godmother raises her disciples."

"What do you mean, there's blood, blood is flowing…!"

However, after several more exchanges, it was Zhao Guo who was tumbling down again.

He kept getting up and charging, but he was busy being thrown far, rolling around, and being pushed back twisted, presenting an unsightly appearance to anyone watching.

"Look there, isn't our Qing'er winning? But what should we do, there's blood. She's hurt."

"The child completely breaks down Movements and knows how to use them. Her mind is clear, and she sees and responds to attacks. It is not an achievement one would expect at that age."

Originally, Movements were practiced as a continuous flow, ingraining their trajectory into the body.

For martial arts learned this way to exert their proper power, one had to take the correct posture ingrained in the body.

But how could that work properly in actual combat where even a speck of dust could act as a variable?

However, as experience accumulates and one understands the principles through actual combat, that was when one reached the stage of freely using any part, breaking it off as needed.

Of course, in Qing's case, she had completely freeloaded.

It wasn't that she knew how to break down and use Movements. Instead, from the very start, what was embedded in her head were completely broken-down Movements.

Moreover, her Physical Stats had surpassed limits.

Her strength, balance, flexibility, and stamina had already developed beyond human levels, so the techniques she used were implemented in the most ideal form as imagined in her mind.

"But that bastard is still fine."

"Though it is just making a lot of noise, she is hitting softly, isn't she? From what I see, it looks like she's training against an Unrestrained Realm master."

The Grand Clan Lord was deducing the situation so well but then stumbled.

If Qing had heard this, she would have questioned whether even Poison Grandfather had gone senile.

Meanwhile, it was also impressive how Zhao Guo still hadn't come to his senses even after being knocked down more than ten times.

Well, to be fair, being unable to handle a girl young enough to be his daughter and rolling on the ground repeatedly, his anger would only grow and not diminish.

As a result, rough thoughts, uneasy glances, and impure murmurs gradually spread among the subordinates of the Embroidered Uniform Guards.

Honestly, it was an unsightly spectacle.

It was in the midst of this when…

Suddenly, instead of charging, Zhao Guo stood still with his eyes wide open in a surprised expression.

"Princess Xialian\footnote{夏蓮, lit 'great lotus'. Haryon (하련) in the original text}? How is it that you are in such a place…"

And then, every time he opened his mouth, it was a series of nonsense.

"That will not do, how can you be in a place like-"

"Y-You must maintain your dignity, your dignity."

"No, no. I too, I also."

"Princess, no, Chuhui\footnote{處𢥁. Chehye (처혜) in the original text}! Hui'er!"

At this, gasps of shock erupted from where the government troops stood.

Princess Xialian was, as her name suggested, literally a princess.

And Princess Xialian's name was not Haryon.

Xialian was not a name but merely a title bestowed by the Emperor.

The real names of the Imperial Family were so noble that merely uttering them was a sin against heaven.

That was why they could not be called by name, so it was the Emperor's august consideration to designate her to be called Xialian.

Nevertheless, he had uttered an Imperial Family member's name in broad daylight with countless people present, which was a terrible capital offense that couldn't be fully expressed just by calling it blasphemous.

Even Wulin practitioners, who knew the Imperial Family like the back of their hand, didn't dare to utter the real names of Imperial Family members.

Zhao Guo's eccentric behavior didn't stop there.

Suddenly, he threw away his sword, pulled at his waist to undo his belt, and roughly pulled down his pants.

He proudly erected his thing for all to see, put his hands on his hips, and began vigorously shaking his waist.

"Haha! How do you like it! For a princess of a country to be so lewd! Chuhui, you bitch!"

To exaggerate a little, it seemed like the sound of blood draining from everyone could be heard as loudly as thunder.

The government officials all simultaneously turned pale, their faces becoming stark white as their pupils trembled.

"You call yourself a princess but you are just a useless whore! This hole is so loose! Even fucking the air would feel better than this, you bitch!"

'Well, he was actually fucking the air, but…'

Everyone swallowed such thoughts to themselves.

"Tighten up right now! You fucking bitch! Who have you been rolling around with besides this Elder Zhao Guo, huh!! Princess, my foot! Was Xialian just a stage name for a whore!!"

As he said this, he kept striking the air with one arm, creating a catastrophe too terrible to watch.

He was so immersed that even as Qing carefully approached to pick up the discarded sword, he was busy just shaking his waist.

Qing pushed all her True Qi into the blade.

Once again, Sword Qi of various mixed colors burst out in brilliant radiance.

Qing stomped the ground, creating a deep depression.

The incredible force in her fighting stance traveled from her soles through her ankles, knees, and waist, adding power as a lightning-fast thrust dug into Zhao Guo's lower abdomen.

Even though he was in a hallucination, it seemed even Force Armor was ineffective in the midst of the act.

Nevertheless, the blade snapped with a crack, unable to withstand the resistance as if stabbing steel.

How could a sword possibly penetrate someone with such a body and Force Armor on top of that?

Is it some kind of special External Art?

Is this the legendary Invincible Vajra Body?

Zhao Guo, with his back and stomach pierced by the broken blade, looked up at Qing with disbelieving eyes.

"Princess? Why…"

\textit{It seemed the drug's effects persisted even with his dantian skewered.}

\textit{Well, if being stabbed with a sword could detoxify poison, what use would antidotes be?}

\textit{Instead of acupuncture, I'll give him one sword-puncture.}

Instead of answering, Qing took a deep breath and shouted.

"How dare you insult the Princess!! I cannot let this slide!! How dare you!! Who was it again, right, Princess Sulian!!! Blasphemy is not allowed! I hate blasphemy! Criminals shall receive castration!"

At the same time, Qing's kick dug between Zhao Guo's legs.

BOOM! With a sound like a wall collapsing, Zhao Guo's body flew up about one and a half stories high before crashing down and rolling on the ground.

This time, the feeling was definitely there.

It was the vivid sensation of pulverization, with the pubic bones on both sides in front of the pelvis and the tailbone area in the back all being shattered to powder.

Above all, the sensation of flesh between the pelvis and instep being crushed and mashed was satisfying, no, truly the very definition of a huge satisfaction.