\chapter{Tang Clan's Paper Flower (17)}

Qing added one more thing with a grin.

"And that includes the Grand Prince Dexian."

At this, Ziyou's expression became ambiguously distorted.

He opened and closed his mouth as if at a loss for words, and finally settled on a self-deprecating sneer.

"Did I not tell you? That person only cared about his own self-preservation. He did not particularly care for the people out of affection, so how…"

"Who knows? When they said the Grand Prince had died, people were sprawled out on the streets wailing and crying. If they're weeping so much for someone whose face they don't even know, doesn't that mean he was an excellent person?"

"But that doesn't mean he was virtuous…"

"Forget it. At least I think so, and those people crying on the streets think so too. If you've fed that many people, you should be able to puff out your chest and brag like a real man."

"Huh."

Ziyou shut his mouth tightly.

He seemed to have a lot on his mind.

\textit{Geez, for a man to be so shy.}

Of course, Qing could tell at a glance, even if no one cried or praised him.

Wasn't Ziyou one of the best people among those Qing had met?

Of course, with the overwhelmingly good Qing among the virtuous, if you compared the two, there would be a difference like the sun and the moon, but since the rest of the good guys were at the level of fireflies, even being a mere moon was a great achievement.

By now, Qing roughly understood by what standards the visible Righteous and Evil Karma were measured.

If you harm people, Evil Karma accumulates and you become an evil person harmful to the world.

But only to people.

Once you turn to Evil Karma and become an evil person, you're treated not as a human but as a pest.

It was a structure where killing or breaking the spirit of a harmful insect was actually considered beneficial to the world and gained Righteous Karma.

However, this Karma thing didn't consider individual circumstances, intentions, or nature.

Even with benevolent intentions, if you ended up pushing countless lives into suffering, you were one of the evils under heaven.

And even with the most wicked intentions in the world, if you made good people live and laugh, you got a big 'Well done!' stamp.

It was a ruthless branding that only evaluated based on results.

But because of that, Qing wasn't ruthless.

If she liked someone, she could look after them like Gramps or Senior Sister Wannabe, or she could pursue personal pleasure through fun dissection practice like with other evil people.

Who decides? Well.

Isn't picking up trash a good deed no matter who does it?

Is it a bad thing to not pick up what's strewn on the road?

If someone says 'You pick up paper but not plastic, you bastard', you can just laugh and say "You pick it up yourself, then'.

The worst bastards were the ones who said it was better not to pick up at all than to do it half-heartedly.

It's not like Qing has a job as a rehabilitation counselor for evil people.

There was no obligation to say all evil people must be cut down harshly, right?

Even that annoying Mission Window just asked what side she would take with these kinds of missions.

It didn't force her to eliminate bad guys.

At that point, Qing's thoughts, which had been going well, took a crooked turn.

\textit{Hmm. It might actually be easier if it forced me.}

\textit{Then I'd at least know why I fell into this world.}

\textit{Not knowing the intention makes me wanna die because of the anxiety}

This was Qing's fundamental fear.

Qing still didn't know how to hold back in front of food.

It was not a matter of gluttony.

It was just that she can't help herself.

She still remembered when she first fell into Wulin.

She remembered how terrifying hunger was.

She knew that when a person was starving, they ended up swallowing even worms and rotten food scraps.

The memory of that time, when she shoved into her mouth filth that would be disgusting to even touch with modern sensibilities, forcibly swallowing it along with rising nausea, sobbing as she ate, remained as a clear, indelible brand.

So she must always keep her stomach full no matter what.

Because as she got endlessly hungry again, as the pain approached, feeling like her stomach was being torn apart, the memory that came back clearly was all too frightening.

It was a dramatic experience where a life that had been relatively satisfied and peaceful suddenly fell into the abyss for no reason, changing to a situation worse than a worm crawling in the gutter.

Because it wouldn't be strange if something that happened once happened a second time.

It showed how terrifying an unguaranteed existence can be.

What if suddenly, lightning strikes because you didn't do as you were told, and the genre changes to something like 'DLC: Eternal Hell Experience'…

At that moment, a warm sensation suddenly rose up.

"Friend? What's wrong? Friend!"

Added to that, Qing quickly came to her senses at the calling voice.

"Ah. Huh? Ah. Heuup."

Only then did Qing realize that she hadn't been breathing.

Even after finally giving wind to her gasping lungs, she couldn't control the trembling, so her legs immediately lost strength and the back of her knees stung and shook.

Qing frowned and forcibly shook off the dirty feeling.

\textit{What the hell, why isn't the Great Meditation Divine Arts working?}

\textit{Wasn't it supposed to block things like this?}

\textit{Why did he had to ask that kinda fuckery? It makes me feel like shit.}

After being hurt in her heart, the words coming out of her mouth were also extremely sharp.

"What do I care about the Son of Heaven or whatever? As far as I can see, he's just a total son of a bitch. If he's an Emperor, he should think about ruling well like an Emperor instead of going on about Wulin this and Heaven that. It's all just about filling his own belly anyway, isn't it?"

"…I wasn't asking you to say such blasphemous things."

"Son of Heaven, my ass. If Heaven sent him down, it would have been to do good deeds, not to sit up high and boast ‘I'm the noblest both in Heaven and under Heaven, I'm the best.' Tell him to fall into hellfire when he dies. Good people should receive blessings and only bad guys should be punished."

In reality, these were words she was saying to herself.

Good people should receive blessings.

‘Only' bad guys should be punished.

To Ziyou, it seemed like an explosion akin to a sudden fire bomb.

In the highly developed psychosocial professional terms of that other world, it was something known as sudden malding.

Ziyou's expression hardened.

To someone who didn't know Qing's inner thoughts, this saw how it would sound.

That she had been wronged by the Emperor somehow and harbored a deep grudge.

Hadn't she said she had no parents?

If such a spirited girl suddenly turned pale with fear, trembling and unable to even breathe, surely it must be related to that.

Moreover… her hand. Hand. Hand.

"Are, are you alright?"

"I'm fine. No. I'm not fine. I feel like I'm going to throw up."

"I see. Then, is it alright if I keep holding on until you calm down?"

"Ah."

At some point, without realizing it, Qing had been tightly grasping Ziyou's hand.

Qing let go in surprise.

Ziyou quickly rubbed his other hand with a somewhat regretful expression as he withdrew his empty grasp.

He had to do this or it would bruise immediately.

It was because Qing's grip strength was no joke.

Qing also blamed others in the uncomfortable atmosphere.

This was all because of Senior Sister Wannabe.

Because when she had that fit back then, the embrace that hugged her was so warm and comfortable.

And after that, even if she looked just a little anxious, she would quickly notice and hug her tightly, so whenever her condition got a little worse, she would seek human warmth.

It seemed only bad habits were forming.

Before, she would just throw a fit alone.

Still, having someone by your side when you're anxious is really the best.

One of the side effects of the White Hand Demonic Arts was that the hands were always cold and emitted a chill.

One of the advantages was that because the hands were always cold, they always felt warm when touching others.

Qing regretted the fact that the remaining warmth left her hand, but then realized there was no need for that.

\textit{Don't I have something like family too? she thought.}

"If you have nothing more to say, may I withdraw now? I'm not feeling well."

"Yes. I too will likely become busy."

Ziyou spoke with a somewhat relieved expression.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Excuse me. Um… Qing'er, hey."

"Huh? What?"

"No. I was wondering why you're like that."

It was a question asking why she was snuggled up in someone else's arms when her legs were fine.

"This is originally what Gramps used to do. If your legs hurt, you just don't stand, you feel?"

It was like saying if you're hungry, you eat.

Tang Lan-ah tilted her head.

But they don't feed you just because you're hungry, do they?

However, since Cui Liweng nodded as if it was natural, she just thought, maybe that's how they grew up over there.

"I didn't sleep well, so I'm sleepy. Gramps, wake me up if anything happens."

"Alright. It is only right that you sleep at night, after all. Go ahead and fall asleep."

And then she somehow managed to lean back and position herself, resting her head and closing her eyes.

She's not a seven-year-old child.

\textit{Is this seriously fine when she's all grown-up?}

Tang Lan-ah kept tilting her head left and right in bewilderment.

The Grand Clan Lord watched this scene with half envy, and then, thinking about it, admitted that the other half was also just envy.

Then he approached Tang Lan-ah and asked quietly, just in case.

"Is Ah'er sleepy too? Should this old man hug you?"

"Hmph, who do you think I am, a child?"

"A child? Look at your friend too. They say beauties are sleepyheads."

"…Still, it's embarrassing."

Of course it was.

It was a skill that couldn't be done unless one had a face as thick as Qing's.

At this, Cui Liweng, for some reason, seemed proud and puffed up.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Listen, Tang Clan Lord."

"Yes, Your Highness. Please speak."

"I have been thinking. If you are considering having a Grand Prince as your backing, release your medical texts."

Release the medical texts.

He was telling them to release the medical arts researched by the Tang Clan to Jianghu.

"Your Highness, however, that is…"

Medical arts were also a strategic resource.

Even with the same serious injuries, superior medical arts could revive and add to the fighting force, so how could it not be called a resource?

"It does not have to be in my name. It will benefit the world, so words praising your clan will spread far and wide. Why do you hesitate?"

"However, Your Highness."

"Saltpeter mines and secret gunpowder manufacturing. Not to mention, it seems you have been researching Thunder Bombs separately? From now on, you can do it openly. How about it?"

He was saying to stop doing it secretly and make them openly under the Grand Prince's name from now on.

It was granting immunity, but in reality, if made openly, the ownership would also go to the Grand Prince.

It was a threat to hand over both medical arts and Fire Bombs.

But if they didn't like it, they shouldn't have done things that could become treason in the first place.

"…We shall release them."

"Do not think too badly of it. I do not know much about medical arts, but who knows? The Tang Clan might become known as the greatest physicians under heaven."

At this, Tang Touzhong's expression improved a little.

Being called a family of benevolent doctors with the best medical arts in the world, rather than poison-eating ruthless bastards, wasn't entirely unpleasant.

Moreover, how could someone with the status of a Clan Lord not know the reason for making such demands at this point?

It wouldn't be bad to use this opportunity to crush not only the Five Noble Clans but even the Nine Sects One Union, and become the leader of Orthodox Wulin.

"Does Your Highness intend to mobilize troops?"

"Everyone looked tired from last night's unfortunate events. It shall be sorted out before the sun rises, so just think about how to raise your damaged assets."

With that, he leaned back on the hastily prepared throne, indicating it was time to withdraw.

After Tang Touzhong left, a shadow from a corner of the underground protruded and approached, swaggering.

"Your Highness. How about this? As a future reconciliation measure between the government and Wulin, nothing beats a marriage."

"Silence, Jiuzhe. How could a Grand Prince stuck in a mere mountain corner speak so grandly of the government?"

It wasn't wrong to call it a mountain corner, since the land of Sichuan was surrounded by naturally blessed mountain peaks.

However, what came out of that corner was abundant products and resources that could easily feed half of Zhongyuan and still have leftovers.

The young man, Yangxiang Jiuzhe \footnote{羊相 舊者, lit. 'sheep face old person'. Yangsang Guja (양상구자) in the original text}, answered with a grin.

"That is right. How could one speak of wedding gifts first when they have not even been prepa… Ow, wait, why are you hitting me? It doesn't even hurt, I tell you."

"Your mouth is truly uncontrollable. That is enough. Now go and tell them it is time. It seems I could not just live relying on Elder Brother's mercy."

"Old Dog must be very eager. He will have to be diligent to fulfill his wish, after all. No, wait, I told you it's useless to hit me. It's the same even if you kick me, Your Highness."
