\chapter{Tang Clan's Paper Flower (5)}

Tang Lan-ah originally had no friends.

Friends were supposed to be equal relationships, but there was no one in the Tang Clan who was on the same level as Tang Lan-ah.

Since Tang Lan-ah was unofficially ranked number one in the Tang Clan, everyone from the Clan Lord to the elders above him were all just worthless beings beneath her feet.

Since this was true within the greatest Sichuan Tang Clan, there were inevitably no matches for her outside at all.

Instead, when she occasionally needed something, she would pull someone up from under her feet to above her head and shower them with cutesy. But recently, the newly promoted(?) 'sister-in-law' had betrayed her and left.

Instead, she gained something similar to a friend (She wasn't sure herself, having never had a friend in her life), so it was a case of 'as one horse flees, another arrives' - the principle that when one horse runs away, another rolls in.

And there was one thing she always wanted to do if she ever made a friend.

Tang Lan-ah arrogantly extended her finger.

"Hey. You."

It was a sudden pointing gesture, but Qing let it slide.

She knew that the child was just a bit rude, but didn't have any particular malice.

These days, the Chihuahua seemed to have been tamed somehow, always hovering around and looking for opportunities to give a treat. As such, how could one hate that?

"What?"

"Sleep with me today."

"Gasp. If you come at me so suddenly like that…"

Qing was startled.

Of course, unlike Chen Changming, Tang Lan-ah was a full-fledged 22-year-old adult, so one could say she had sexual autonomy.

As Qing drew back, Tang Lan-ah's eyes shot up.

"What? You don't want to?"

"How can a young lady say such things when men and women should be separate?"

"What, you don't want to…?"

The same words, but this time her shoulders slumped and her expression fell into a frown.

Tang Lan-ah asked again.

"You… aren't close to me…?"

"If we had to be so black and white, I suppose we'd be on the close side?"

"Then why? Aren't close friends supposed to sleep together?"

"Oing? Why is that? Is that the culture in Zhongyuan?"

"Ha. How ignorant. Have you not even finished the Basic Teachings?"

According to the Basic Teachings, a textbook for children in Zhongyuan, it explains the righteousness that siblings should practice as follows:

When sleeping, cover with the same blanket, and when eating, share the same table.

Using separate clothes and food between brothers is something only barbarians, not human offspring, would do.

At this point, one can see that Zhu Xi, who compiled the Basic Teachings, was both a Master of Neo-Confucianism and a serious racist.

However, in this era, discrimination against barbarians was natural for both those doing it and those receiving it.

It was an era where folk tales like 'I gave a kind word to a barbarian, and later they repaid me with my life' were widely spread.

At any rate, he didn't create Neo-Confucianism but rather compiled it.

The Basic Teachings was not a novel but a compilation, a children's recommended book that beautifully collected the virtues of that era.

Just look at the part about sleeping in one bed under one blanket.

To put it roughly, even a thousand years before Zhu Xi lived, sharing one bed and one blanket was a beautiful story of siblings with the highest fraternal affection.

After all, the famous Three Sworn Brothers of Liu Bei in the Romance of the Three Kingdoms spread their reputation for brotherhood by sharing one bed.

Liu Bei often used this when winning the hearts of his subjects, saying ‘Stay and sleep with me tonight' would cause a flood of tears and loyalty.

It was a scheme to give the impression of ‘Ah! My lord considers me as a brother!'

Of course, normal people wouldn't shed tears of joy when a man tells them to stay and sleep.

Sharing one bed and one blanket was closer to filial piety for parents who found it difficult to prepare separate rooms for their children.

However, the boasting of the Chinese people was a cultural trait.

They would follow famous stories or anecdotes, and then use the aftermath to elevate themselves, saying 'I am a person who did this much.'

Thus, even the subjects who slept with Liu Bei made it a point of pride to pass down to their children for generations, saying 'Listen, your grandfather/ great-great-grandfather/ ancestor slept with Liu Bei!'

As an aside, in terms of friendship in Zhongyuan, Sun Ce and Zhou Yu were actually considered above Liu Bei's Three Sworn Brothers.

They were famous for their original close friendship, even abandoning their wives to share one bed, but they weren't very popular among the Korean people, so they weren't well known.

"Ah. What? So that's what it was?"

Qing realized her misunderstanding.

\textit{So it's not that kind of sleeping where they say, ‘We'll just hold hands, okay?', huh.}

\textit{It's not that kind of sleeping where people hold hands but eventually do this and that. It's literally sleeping in the same space while chatting. It's that kind of culture, huh.}

\textit{But what does brotherly love have to do with friendship?}

Qing thought this because she didn't know.

In fact, in Zhongyuan, deep friendship was used to mean the same thing as brotherly love.

The unique culture of the Chinese people, Guanxi, was even legally codified (It wasn't) and had detailed, systematic levels.

Guanxi Level 1, Friend (朋友) was an acquaintance.

Level 2, Good Friend (好朋友) was where friendship starts.

Level 3, Old Friend (老朋友) was where Guanxi expansion began, and it was the level where introducing acquaintances becomes possible.

In terms of martial artists, this would be equivalent to First-Rate.

And only at Level 4 did it reach family, called Brother (兄弟).

From this level, even if it was just Guanxi, they were called family, so it becomes a stage where one couldn't casually end the relationship.

Achieving Level 5 made one Sworn Brothers (干兄弟).

This was the highest level and a legendary achievement.

Uniquely, Sworn Brothers were above Brothers, meaning that Sworn Brothers chosen by one's own judgment were more intimate than actual Brothers who could not be chosen.

It was also characteristic that the terms change according to age and gender, such as Sworn Brothers, Sworn Siblings, Sworn Father, Sworn Mother.

Of course, Zhongyuan were still primitive China, so they weren't as formalized as that certain country from Qing's origin.

To put it simply, it was still more of a feeling that one had? So it wasn't yet the age-old malpractices of the rigid future Chinese.

Tang Lan-ah saw through Qing's state immediately with the intelligence of a doctor of traditional medicine.

Even without a doctor's intelligence, anyone with eyes could see Qing's expression of not understanding a single thing.

"Originally, it's common sense for friends to sleep in one bed under one blanket, you know? Don't you even have friends?"

"Huh? That's common sense…? Come to think of it…"

Thinking about it, the female friends Qing had made in Zhongyuan always coveted her bed.

Chen Changming would appear every night hugging a pillow, and Senior Sister Wannabe tried a few times before giving up and just coming in the morning to change her clothes.

Qing was unsure.

Same-sex friends could share a bed, but that obviously couldn't be common sense.

It was Tang Lan-ah's wicked lie trying to raise the level of friendship at this opportunity.

Though her appearance was beautiful, she was actually a wicked woman who didn't discriminate in her methods to achieve her goals.

She was a scary child who could tell such che-, no, horrible lies without even batting an eye.

Her evil deeds could be compared to those of the greatest Demonic Adepts under heaven.

Qing looked at Tang Lan-ah, who was fidgeting and didn't know what to do.

\textit{Well, of course she'd be anxious when her family is in danger.}

\textit{Even Young Lady Peng told me to take good care of her, so.}

\textit{It was also pitiful to see her clinging and asking to play all day with slumped shoulders because there were no patients.}

Qing grinned and answered.

"No friends? Obviously, not. If I were to list the people I could sleep with, the queue at the Divine Maiden Sect's training ground would wrap around two and a half times in the formation of a parade."

Qing said this as a joke.

However, if it were actually done, a similar scene would probably unfold. Not that Qing knew this, of course.

At this, Tang Lan-ah's expression immediately brightened.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had picked up several bad habits since entering Zhongyuan, including some very undesirable habits in the bedroom.

"W-What, why are you undressing…!"

"Huh? Should we sleep with clothes on? Why?"

"Huh?"

Tang Lan-ah had no chance to object as Qing spoke as if it was such obvious common sense.

Qing herself was completely unaware, but she had reached a state where she was no longer shy around women.

She had forgotten shame while running around half-naked in the Divine Maiden Sect, and later accepted being taken care of as natural during her life in the Bliss Palace when she went crazy.

On the other hand, she wasn't shy around men either.

When she saw a woman, it was just a woman's body, so so what?

When she saw a man, it was just between me, so so what?

Wasn't she also in a bizarre state when her body was briefly stolen by that mental parasite of a Heavenly Demon before?

The Heavenly Demon's mind was in the form of the First Generation Heavenly Demon, but Qing's subconscious chose the appearance of A-Qing, not the production worker from before her journey into Wulin.

This was a fact that Qing herself hadn't realized.

In Eastern terms, one could say that the mind is water and the body is the vessel, so the water takes the shape of the vessel.

In Western terms, one could add explanations about hormones and such that liberal arts majors couldn't understand.

But since there wasn't even a single person in this world who could explain it logically like this, it would remain a distant matter for the foreseeable future.

If Ximen Surin had known, she would have beaten her chest in frustration.

'How can this half-wit who can't even define her true self, her genuine self, achieve the Transcendent Realm?'

The Transcendent Realm meant transcending the Peak Realm.

The Peak Realm referred to the highest point an individual could reach, so the Transcendent Realm was the first step in transcending oneself.

Thus, the mind that had overcome itself contained the will of the stars, that starlight, and wielded it. This was called Sword Force.

The word ‘Force', also known as ‘Gang', in Sword Force meant the constellation, the Big Dipper.

It was called Sword Force because the most destructive power wielded by martial artists was the will of those stars, the starlight (光/ 'guang'/ light) emitted from the human sky without the sun.

As an aside, in Qing's homeland, there was also a rather sad case of using the character for 강 (剛/ 'gang'/ strong) instead, because the primitive computer Korean character arrangement couldn't display the rare Chinese character.

Anyway, Qing rubbed her bare arms and legs on the bed and exclaimed in admiration.

"Wow. This bed is nice. It's like actual silk."

"Well, it is silk…"

It was practically the most expensive bed in Sichuan, so there were few better beds even in Zhongyuan.

Qing couldn't help but admire its comfort.

"Is that so? Well then, I'm going to sleep, okay?"

"Wait, how can you do that? At least have some conversation or…"

Qing thought.

\textit{What the… How annoying…}

"You should only sleep in bed in the first place. If you do other things, it gets ingrained in your mind and leads to sleep disorders, and further to insomnia."

"What's that? Forget it. Qing'er… do you perhaps have a man you love or admire?"

Tang Lan-ah slipped in a term of endearment.

Qing was ignorant about Zhongyuan terms of endearment, so she thought it must be because Young Lady Peng called her that too.

"I don't."

"Huh? Then what about the Jade Qilin?"

"He's just a friend? To begin with, that guy doesn't like women."

"Gasp."

Tang Lan-ah inhaled sharply.

\textit{To think there was such a secret about the Most Handsome Man Under Heaven!}

If Peng Daesan had heard this, he would have raised an eyebrow and lowered his voice to the depths of the deep sea.

But Peng Daesan wasn't present.

And they say you can even criticize a king when he's not around.

(Though they still wouldn't criticize the Son of Heaven)

"I thought so. There were such rumors, after all."

"It's not about rumors, you can just tell by looking, can't you?"

"But when I saw him, hmm? Wait, maybe you're right? Huh, wait, you're right."

Tang Lan-ah had seen him once at the Dragon and Phoenix Assembly held in Sichuan, and again at the Grand Clan Lord's 70th birthday, but at those times she was blinded by his radiant appearance and didn't notice at all.

Thinking back on it now, his gaze towards women was a bit off.

And then Tang Lan-ah felt a chilling sensation-

No, wait it's actually cold!

Cold autumn night air was seeping in through the gap where the blanket didn't touch the bed.

"Excuse me, can you give me some of the blanket…?"

"Ah. I've gotten into the habit of rolling myself up. Can't we just use two blankets?"

"No. It clearly said one bed, one blanket. But why? Wouldn't we have to sleep close together then? But why? When there's such a wide bed?"

In fact, sleeping close together is the essence of friendship.

But in the common sense of Tang Lan-ah, who had never experienced a journey into Wulin, beds were originally large objects made spacious enough for ten people to lie down.

She couldn't help but wonder why they had to use one blanket on such a wide bed.

There was no way Qing would know the answer.

But since it wasn't really a question seeking an answer, Qing just threw out any response.

"Maybe there are special extra-large blankets for friends?"

"But then it would be heavy. And stuffy."

"If two people support it, the weight is halved, right?"

"Is that so? Are there sizes for different numbers of people? Hmm. I should tell the servants to bring some in."

They exchanged the kind of conversation that only idiots would have.

But conversations between friends are usually a series of such things, so they were essentially just enjoying themselves.

"Hey, you, the blanket again, let me use some blanket too."

"…"

At some point, Qing's breathing deepened into a wheeze and her head lolled over.

Qing was a sleep expert who could quickly fall asleep even in Cui Liweng's swaying arms, so on this soft, top-quality bed that just enveloped her body, she eventually passed out.

"What the… You're asleep? Already? Geez, why is she so strong? I want some of the blanket too, it's cold…"

With Qing's Xiang Yu-like strength gripping the blanket, Tang Lan-ah had no way to take it back.

As such, she had no choice but to move closer.

Then at some point, there was a big movement as if turning over, and something heavy pressed down on half her body.

As a hot breath immediately tickled her earlobe, Tang Lan-ah was startled and froze up.

"Gasp. Hey, hey…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The next day, Tang Lan-ah's complexion was haggard.

Of course, nothing unseemly or untoward had happened during the night.

She just hadn't slept well and was a bit tired.

Even as she entered the Tang Clan's strategy meeting for the final battle with the government, which started from early morning, she looked visibly exhausted.

Qing, of course, participated in the meeting without much thought, as she was now virtually treated as the clan's benefactor and savior.
