\chapter{Tang Clan's Paper Flower (19)}

"…I'm hungry. Gramps, is there anything to eat?"

That was the first thing Qing said as she opened her eyes.

Then she looked around.

It was already daylight, and she was on a bed where sunlight was streaming in.

Beds in Zhongyuan were scientifically designed to let sunlight fall on one's face from mid-morning to noon, after all.

And outside, there were busy sounds.

Sawing, hammering, walking, dragging…

Qing roughly put on her clothes and tied her hair as she stepped out of the bedroom.

Cui Liweng, who was sitting on the porch looking outside, naturally followed behind, so Qing gave a morning greeting.

"Gramps? Is there anything to eat? I'm hungry. Aang."

It was a morning greeting as if she had entrusted him with finding food, but something immediately entered her mouth, causing Qing's eyes to widen before narrowing into pretty lines.

Sticky, crunchy, savory, and sweet.

It seemed to be a type of pastry with nuts.

Qing stuffed the snack into her empty stomach while watching the busy construction work at the Tang Clan.

Cui Liweng watched her contentedly.

"Did something happen last night?"

"Nothing much. The government troops withdrew."

"What? How anticlimactic. They acted like they were going to attack."

In truth, it wasn't anticlimactic at all.

The Imperial Guard was annihilated, the Imperial Censor and the Eastern Depot Eunuch were captured, and the Embroidered Uniform Guard was about halfway between annihilation and capture.

"Ah! Young Miss! Aren't you Young Miss Ximen!"

"Oing? Who are you? Do you know me?"

"This humble one is called Chuanglan Jinhu. You can just call me Fox. Hehe, though late, I'll pay my respects."

And with that, he prostrated himself on the ground.

"Are, uh… are you okay?"

Qing asked, looking at Fox's face.

She didn't know what his original face looked like, but it seemed to be swollen two to three times its normal size.

It looked like he had disturbed a beehive, with dark bruises and bumps all over.

"Oh my, to even worry about this beast. How can your heart be so kind? But please lower your speech. You do not need to use honorifics. Hehe, this lowly one is dazzled in front of Young Miss, if you raise your speech too, my pea-sized gall can't handle it."

"Uh. Um, okay…"

Qing obediently listened.

She thought he must be a servant of someone in the Tang Clan.

Qing didn't know how to refuse.

"Hey, you fox bastard. Where are you going so early in the mor- Ah, that person is! Young Miss, is it Young Miss? Oh my goodness, how beautiful! Oh my, I shall pay my respects."

Another servant came and immediately knelt down.

"What's going on, why are you all- Ooh!"

"So it's that person!"

"I can feel an amazing aura!"

And then, like minions greeting their boss, servants appeared one after another to pay their respects, kneeling and bowing their heads, their numbers gradually increasing.

"Truly a noble person. Looking with this Daoist's Spirit Eyes, I can see that the rank of your soul is so high that a refined spiritual pressure flows from you."

"Hey, Fake Daoist, is that right? How can someone who can't even find one water vein talk about Spirit Eyes? In Sichuan where water springs up no matter where you dig, you failed seven times in a row. What kind of Daoist are you?"

And so a group of people gathered, politely taking their places in the front yard, bickering and squabbling as they held a competition to see who could flatter better.

"In last night's dream, as I was walking and about to pick up a piece of jade I saw on the road, suddenly the brilliant Vermilion Bird rose up with five-colored radiance. Isn't this a dream of meeting the noblest person in the world? Indeed, I can see at a glance that Young Miss is such a person!"

"This bastard, always going on about Vermilion Birds. What happened to the Azure Dragon, Black Tortoise, and White Tiger? Did you sell them off somewhere?"

"Excuse me. It's a small thing, but…"

A servant with his face completely hidden by hair quietly approached and held out a small box.

When opened, lo and behold, a jade bracelet thicker than a finger hole revealed itself.

Qing's expression soured as she quietly pushed it back, thinking that some gifts were a bit much.

"It seems very expensive."

"I just picked it up on the road, so don't worry about it…"

"No, what? Why would something like this be lying around? I don't lack that much awareness, you know? Go pick it up again."

"That gnat-like bastard is offering a bribe!"

"Booo! You cheap bastard! When did you prepare that!"

"Hmm. It can't be helped. Madam, do you perhaps enjoy calligraphy and painting? This brush is made from the tail hair of a white marten from Mount Bei. When it comes to brushes, the finest hairs are the best, aren't they? I've only used it once for a test writing, so it would suit a noble person like you better than me…"

And then they rushed forward, placing their precious items before Qing as if offering tributes, and before Qing could refuse, Cui Liweng swiftly intercepted them and piled them up behind his back.

That's when it happened.

"What are you all doing so early in the morning! Don't you have work to do?! If not, you should at least help with the construction! Get lost, all of you!"

An extremely stern-looking old woman appeared and shouted, causing everyone to scatter in fear without hiding their terror, disappearing without a trace.

"Uh, who are you?"

"Hmph. I haven't acknowledged anything yet. But thanks to you, the man has conceived a grand dream, so I am grateful for that much."

The old woman, Hag Yan, clicked her tongue inwardly.

The hidden dragon who wanted to live quietly was now aiming for ascension, but if the goal was just for one woman, wouldn't it be laughable to the world?

Still, gratitude was gratitude.

Thanks to this, they had eliminated three thousand Imperial Guards, wiping out three thousand of the Emperor's most elite soldiers.

In addition, there was the Embroidered Uniform Guard Assistant Commissioner and thirty martial artists.

They had driven the family of the Imperial Censor, the head of the Censorate, to extermination, and as a bonus, removed the Eastern Depot Eunuch.

These were all blades that the Emperor could wield directly, so it was like cutting off one of his limbs.

The Emperor's power had collapsed significantly.

With this much, it was enough to aim for a great undertaking.

"However, when one's position changes, so does their perspective. If things go well, he will return. Even if they don't, there's no need to feel disappointed with that much."

Hag Yan coldly threw something.

It was a book without a title, and when Qing touched it, the Martial Arts Window immediately flashed, announcing the registration of a new item.

It meant she had touched a complete secret manual, indicating that this book was indeed a martial arts secret manual.

"This is…?"

"It's something that once caused a bloodbath in Jianghu, so it would be best to keep it hidden from others."

Hag Yan looked at the book with somewhat regretful eyes.

It was a gaze filled with long-held resentment, as much sorrow and self-reproach.

But that was only for a moment, as she turned around with a "Hmph" and walked away proudly.

Qing tilted her head.

So, who were they and who had they been…?

Anyway, when Qing checked the Martial Arts Window, the newly registered… \textit{My goodness! Purple, why suddenly purple?}

\textit{Moreover, it's a Purple Movement Technique called Wave-Treading Subtle Steps!}

\textit{Hmm, I've never heard of this before.}

It was because Qing's knowledge was too lacking.

And then the Mission Window went crazy.

\textit{What's going on? Why is everything taking turns going nuts?}

\begin{quote}
[Struggle of the Yellow Dragon The Beginning Chapter. (Unknown)th Crisis]

Description: [You have been caught up in the power struggle of the Imperial Family.]
\medskip

Decide your course of action.

[This choice may influence everything under Heaven.]
\end{quote}
This time, there was just one line about deciding factions without even saying what to do.

\textit{If you suddenly do this, what am I supposed to do?}

Qing just dismissed the Mission Window and decided not to think about it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After that, a joint funeral was held at the Tang Clan.

Personally presided over by the Grand Prince, it was a joint funeral to honor the forty-two loyal and righteous members of the Tang Clan who fell to artillery fire while resisting the rebel faction impersonating Imperial troops to protect the Grand Prince, and the one hundred and seventeen loyal and righteous soldiers who lost their lives in the process of suppressing the traitors.

After the funeral, a huge monument was erected at the entrance of the Tang Clan's main gate, engraving their names.

Among them were faces Tang Lan-ah knew, and she showed quite a gloomy appearance afterward.

It did look pitiful.

So even though she was being particularly clingy, Qing let her be, thinking she must feel quite down since people she knew had died.

"Hey."

Tang Lan-ah immediately pressed both knees, the tops of her feet, her forehead, and the underside of her forearms to the ground.

It was a grand bow with discipline and force, no matter how one went about it.

Qing's eyes narrowed as she looked down at the back of her head.

"Hey, why are you fondling someone else's chest?"

It is only right that if a tail is long, it would get caught.

Tang Lan-ah, caught red-handed, bowed her head in a grand apology bow in the middle of the night.

"No, I just, it just felt nice and soft. At this age, it's awkward to do this to my mother. And my mother's aren't that big anyway…"

Tang Lan-ah didn't particularly have any other intention.

At first, she had just wondered how something this big could stay attached without sagging and feeling how incredibly soft it was, but somehow that texture wouldn't leave her mind day and night.

"Shit, you have your own. Why are you messing with mine instead of your own?"

"But the feeling is completely different. It's like, there's none of this sinking feeling. And it's not like it's going to wear out. Don't be so stingy. Friends can touch each other a bit."

Tang Lan-ah rather boldly stepped forward.

Qing had seen things in the Divine Maiden Sect too.

In fact, she knew that women liked large breasts just as much as men did.

Disciples with suspicious sexual preferences tended to be more reserved, while normal disciples were much more persistent in coveting others' chests.

It was to the point where she would invariably see disciples with large chests complaining and telling others to stop at least once a day.

There were even about four disciples who fearlessly asked if they could touch a great elder's chest just once.

(Of course, Qing didn't receive much treatment as a great elder besides for her title and status, being an outer disciple and a comfortable peer)

Qing's eyes narrowed.

"That doesn't mean you can secretly grope."

"Ugh. But if I ask, you'll say no."

"Of course you can't. Do you know how ticklish it is?"

"Hmph."

"What do you mean ‘hmph'? You're in big trouble now. Kneel down and raise your hands."

Anyway, Tang Lan-ah, feeling guilty, obediently followed those words.

It was also because she knew from numerous experiences that it was beneficial to quietly listen at times like this.

Forgiveness is easier than permission!

It was Tang Lan-ah's vicious mindset, learned through the many misdeeds she had committed over a long time and the apologies that followed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And so, Qing's days of playing around under the pretext of fixing her split chest continued for about a month.

And then there was a woman who came to see Qing.

It wasn't Senior Sister Wannabe, whom Qing wasn't particularly waiting for or even thinking about!

She was still in the middle of crossing the continent.

The Demonic Cult was too far away.

Moreover, it was a journey with no need to hurry.

So she was leisurely enjoying her first trip to Zhongyuan, spending the generous travel expenses given by the Divine Cult freely, with Xue Ganom as a guide by her side.

The one who came to see Qing was another woman.

The woman's eyes were somewhat unfriendly as she looked at the large memorial stone erected next to the Tang Clan's huge main gate.

And then she naturally spoke down to the Tang Clan warrior guarding the main gate.

"I heard my disciple is staying at the Tang Clan. Is there not a girl named Qing with the surname Ximen here?"

At this, the Tang Clan warrior froze.

"Young Lady Ximen is staying here, but if you say you are her master, could you perhaps be…"

"Yes. Who is the current Tang Clan Lord now? Was it that smooth-talking child Tang Touzhong? Go and tell him that Senior Ximen Surin has come to find her disciple."

The Zenith Among Women had personally come to find her naughty disciple who had left home and not returned.