\chapter{Tang Clan's Paper Flower (10)}

The Imperial Censor grabbed the back of his neck.

His fleshy build seemed like it might collapse with just a little more stimulation, so Qing was about to push harder.

"That is enough."

The Guard Assistant Commander, who had been maintaining his composure until then, suddenly intervened.

"Imperial Censor, please calm yourself. Is this not just the antics of a green girl?"

But Qing had no intention of ending it yet.

In this kind of battle, the one with the loudest voice ultimately seized victory.

Just as Qing was taking a deep breath…

A shining bead rose subtly above the Guard Assistant Commander's hand and then faded away.

It was Force Compression, the symbol, pride, and crystallization of the Unrestrained Realm.

Qing was quite the consistent person; she didn't act bold in front of the strong and shrank as always.

\textit{What the hell is this?}

\textit{Just when I thought I could handle at least a Transcendent Realm, now this Unrestrained Realm bastard shows up to block my way.}

\textit{Why do Masters keep popping up from everywhere?}

Qing didn't know, but it would be stranger if the martial prowess of the Guard Assistant Commander, ranked third among the Imperial Palace martial artists, wasn't at least at the Unrestrained Realm.

After all, he was a Master deliberately nurtured by the Imperial Family.

Qing stepped back at this display of skill.

Since she had already enjoyed beating them one-sidedly, she didn't feel too regretful.

However, the opinion of the person who had just been beaten up one-sidedly was different.

"You wench! Is it you who learned such dirty slander and stinking lies from your parents?!"

But it was a grand miss.

Insulting her parents were already ineffective against Qing.

To begin with, she was uncertain whether this body was born under human legs.

It might have just been formed from energy coalescing in a cave, or it might have opened its eyes after inhabiting an abandoned corpse.

Since no traces of another mind were found during the mental parasite's invasion, she only knew that she hadn't stolen the body of a normal living girl.

Qing answered with a bright smile.

"This body truly has no parents, you know? I never learned from anyone to begin with."

At this, the Imperial Censor quickly interjected.

"So you were an orphan wench! I thought as much. Yes, that is right. Even I would have abandoned a crazy thing like you!"

"But. I think it's better to be abandoned than to have parents who mated with pigs anyway. How could you live with your face up, being embarrassed about having parents who mated with pigs? If it were me, I would have committed suicide long ago by sticking my face in lye water… no, since it's the Imperial Censor's house, in pig slop."

"You…!"

"EVERYONE! WHAT DO YOU ALL THINK! WOULD YOU RATHER LIVE AS THE SON OF A WOMAN WHO SPREAD HER LEGS FOR A PIG, OR JUST LIVE ALONE AS AN ORPHAN?!"

In a way, Qing's attitude could be said to be the true posture of a martial artist.

At least Qing knew when she was outmatched and immediately retreated to wait for the next opportunity.

The Imperial Censor, despite not being good with words, tried to argue back and ended up stumbling without even getting his money's worth.

At this, the Guard Assistant Commander stepped in again.

"I told you that is enough."

"No, wait, that pig, I mean Dong Zhuo, I mean Zhu Bajie\footnote{A pig-man character from Journey to the West. He's a disciple of Tang Sanzang, along with Sun Wukong and Sha Wujing}, I mean Imperial Censor was making a fuss earlier and you were quiet, but why are you lowering your voice only when I speak… hehe, I'll shut up now."

Qing prettily closed her mouth in front of the Force Compression.

However, her expression continued to smile brightly and cheerfully, persistently targeting the Imperial Censor's blood pressure.

"For such a young wench, your realm is not low, but that venomous heart is even more frightening."

"Hmm. Thank you for the compliment?"

"Rather, it is a pity. If you had not been born with the Tang surname, that of those great traitors, you could have surely made a name for yourself in Zhongyuan."

"Ha. Who's a great traitor? You're accusing innocent people of being criminals without any evidence. Your parents must be so proud of you. 'Son! Today you've once again killed innocent people by wrongfully accusing them of crimes!' How admirable! Your ancestors in hell must be burning in hellfire with pride!"

"…What did you just say?"

"What? Did you stuff a donkey's cock in your ear? Or was it a dog's cock? Since you're taking the pig's side, maybe you stuffed a pig's cock in there? Is your ear hole blocked with a cock so you couldn't hear? Everyone here heard it, but the Unrestrained Realm Master couldn't?"

The Guard Assistant Commander's eyebrow twitched.

"Ah. I think it would be better to throw your parents' graves into a river or the sea instead of burying them in the ground. They'll be burning forever for the sin of raising such a vicious child in the world, so soaking them in water might help with the heat a bit."

"You wench. You are truly courting death."

Qing snorted.

"You're just an incompetent fool lowering his voice. Unrestrained Realm Master? Is there only one retard of an Unrestrained Realm with a cock stuffed in his ear here? Why has this human scum of a butcher, who should have drawn his sword and cut everyone up long ago according to his words, been enduring until now?"

"You wench. You will absolutely not die peacefully. Not until you beg to be killed."

"Wow!! Look at that! Elder Imperial Censor! Did you see that? When you were being insulted, he just lowered his voice saying ‘That is enough' because it wasn't about him, but now that he's being insulted, he's getting angry?"

The Imperial Censor was still red, but after hearing those words, his gaze towards the Guard Assistant Commander wasn't friendly either.

After all, what she said was true.

Qing stepped forward, raising the stakes even more.

"Stop talking and come at me if you're so upset. Fair and square, one-on-one. Like a real man. Want to have a life-or-death duel?"

At this, Tang Lan-ah quickly grabbed Qing's wrist.

"Hey, you. What are you trying to do?"

"It's okay. Just enjoy the show."

Qing's expression was full of confidence as she answered.

Qing was originally someone who valued her own life terribly, so she didn't move on a whim.

But she couldn't tell Tang Lan-ah that she had already prepared some dirty tricks in advance, so she just threw out some cool words.

"I can't just stand by when my friend is being insulted. Right?"

"You, you…"

It was truly a scene of emotion, the back view of someone stepping into danger to protect another's honor.

Wasn't this the image of the most admirable man that women dream of?

Though Qing wasn't actually a man, of course.

Tang Lan-ah's eyes became misty.

However, she was wearing a veil, so Qing couldn't see it.

Regardless, the Guard Assistant Commander was completely dumbfounded.

"A mere Peak Realm wench dared to say what?"

"I said let's have a match. How about it, one-on-one?"

The Guard Assistant Commander snorted through his nose while his mouth stretched into a long grin, not hiding his evil intentions.

"Ha. You wench have truly decided to die! Fine! You said a life-or-death duel, right! You have already said it, so you cannot blame me for what happens!"

"Good. Just don't run away. If you're going to run, you'll have to leave behind what's attached between your legs."

At the same time, Qing walked forward gracefully.

Then, in a manner that didn't suit her, she took a respectful clasped hands posture and shouted.

"This girl is called Qing and has no other title yet. I have studied the Yue Maiden Sword and Divine Maiden Divine Palm, as well as other miscellaneous arts and skills."

After that, she drew her sword and demonstrated some simple movements, then waved her hand in the air a few times to slightly reveal the subtleties of her Hand Arts.

This was called a person's Starting Ceremony.

It was the act of briefly introducing oneself and demonstrating learned martial arts before a duel, and while it was incomprehensible as to why it existed, it was also a long-standing tradition of Wulin.

For a moment, everyone in the courtyard fell silent.

'What did I just see?'

The girl who had been spewing terrible curses suddenly acted like a righteous female expert of Wulin, with every gesture and movement of her fingertips and toes exuding an impeccable grace.

The beauty that had been hidden behind her vicious speech finally revealed its presence.

Amidst the silence of the crowd, the Guard Assistant Commander also stepped forward and performed his Starting Ceremony.

"I am called Zhao Guo \footnote{Cho Gwak (초 곽)}, and I have reached my realm with the Imperial Grace's Demon-Conquering Sword."

At the same time, he demonstrated some simple movements, but anyone could see that it was actually the Demon-Conquering Sword Technique, a supreme technique of the Kongtong Sect.

In fact, the martial arts of the government were ones that the Nine Sects and One Union had offered when they were the government's hunting dogs in the past.

Although they say they were somewhat degraded versions, those degraded Divine Arts all remained in the Imperial Palace Martial Vault, so the Embroidered Uniform Guards, who were Masters nurtured by the Imperial Palace, were made to learn them.

They claimed to have improved them somewhat, adding names like 'Imperial Grace' this and that in front, referring to the Emperor's grace.

The Tang Clan elders who were aware of the situation clicked their tongues, while Qing, who didn't know, wagged her tongue instead.

"Ah, right. By the way, my master is Daoist Ximen Surin, and her Daoist colleagues of Wulin call her the Godmother or the Zenith Among Women."

"…Wait, what did you say?"

"Have you still not removed the cock from your ear hole? I said my master is Daoist Ximen Surin, known as the Zenith Among Women."

"No, no, wait. I have not heard anything about that."

"For your information, my master promised that if her disciple were to be harmed during her journey in Jianghu, she would take revenge a hundredfold afterward. So if anything happens to me, you'll incur the wrath of the Zenith Among Women and your entire clan, down to the last relative, will be annihilated."

Guard Assistant Commander Zhao Guo doubted his ears for a moment.

Normally in these situations, didn't one say there would be no repercussions even if they died? He wondered if he had misheard.

However, while Qing enjoyed deceiving others, she wasn't good at outright lying.

Especially not in her master's name, of all things.

Ximen Surin had actually often joked, mixed with curses, that, ‘Even if you die, I shall take revenge a hundredfold, so do not feel too wronged if something bad happens'.

However, it was a joke mixed with a lot of sincerity.

In other words, it was a petty threat saying that if 'you mess with me, the Zenith Among Women won't leave you alone'.

It was a shabby threat made after requesting a life-or-death duel and performing the Starting Ceremony.

In fact, Zhao Guo's mind went dizzy.

"H-How can a disciple of the Divine Maiden Sect get involved in the affairs of traitors!"

"Involved? This girl was merely staying as a guest. Rather, weren't you the ones who blocked the entrance so we couldn't leave? I only stepped forward because I couldn't bear to see my innocent friend being insulted, so why don't you take back those terrible words about treason?"

Then she extended her hand and pointed at Cui Liweng.

"And that old man over there is taking care of me, and he cherishes this girl like his own daughter. He's currently suffering from senility, so even if something unfortunate happens during the life-or-death duel, I ask for your generous understanding."

As if it wasn't enough, she even laid out an outright threat implying that Cui Liweng might launch a sneak attack.

"W-What, what kind of life-or-death duel is this! How can you use such vile and cowardly tricks!"

"Vile and cowardly? A person who has reached the Unrestrained Realm is calling a life-or-death duel with a Peak Realm martial artist vile and cowardly?"

Qing spoke, full of mockery.

Zhao Guo, at a loss for words, could only open and close his mouth.

At the same time, he realized he had fallen into a trap.

It was called a life-or-death duel, but the situation had become such that if he didn't subdue Qing gently, the consequences would affect not only himself but his entire clan.

"Wait, this is invalid-"

"No more words! Here I come!"

Qing cut off Cho Gwak's words and charged forward with her sword leading the way.