\chapter{Tang Clan's Paper Flower (18)}

Grand Prince Dexian cut down the Emperor's minions coming to Sichuan.

He eliminated the risk factors for his survival.

However, there was something even the Grand Prince didn't expect: Sichuan was the wealthiest land in Zhongyuan, and the officials coming to such a precious post were far from upright.

A good post wasn't a responsibility to govern well, but a reward or gift given to favored officials.

Since the position became a fitting reward given as a result of their conduct rather than a duty shouldered by the office, everyone just enjoyed it without doing any work.

Cutting down such corrupt officials wasn't difficult.

Just one look in their warehouses was enough to immediately behead them.

One word about how they dared to steal from the country, and that treason suited them better than being civil servants, was enough.

When the Emperor heard the news, he raised an eyebrow saying 'What do we have here', but he couldn't say much against executing corrupt officials.

After this purge of corrupt officials, those who remained in office with integrity and ambition took real power.

And these holders of power worshiped the Grand Prince with fervent admiration, so the tripartite system of administration, law, and military that should have been in opposition (the concept of political separation surprisingly existed since ancient times) became united in serving one person.

This was the reason why the Regional Military Vice Commissioner and Regional Military Assistant Commissioner suddenly changed after Yangxiang Jiuzhe secretly entered and left the Sichuan Command Post.

After strangling and imprisoning the Regional Military Commissioner, the twelve thousand troops of the Sichuan military mobilized by imperial order showed suspicious movements.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The guests of the royal household melted away in the night.

These were people who made the royal household their home to escape the world.

They chose shameful and insulting names to call each other, as if making a pact not to call each other by name unless they were family members of the royal household.

It was fine for family to say 'Hey, you idiot' to each other, but if a stranger did it, wouldn't it be a matter of fighting to the death over their honor?

Look no further than the names of the houseguests Qing had seen.

Old Dog, Hag Yan, Sheep-face Jiuzhe, and Spear Woman. Upon seeing such names, there wasn't any need for further explanation.

When the eccentrics of the royal household walked out proudly with the character "Chin" (親, meaning royal) on their shoulders, not one of the Sichuan soldiers tried to stop them.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Imperial Censor stamped his feet and spewed anger.

"What is going on here! Chuanglan Jinhu, you bastard! Didn't you say you personally recommended the poison- no, the medicine to His Highness!"

"Of course! Didn't the Esteemed Censor himself confirm the corpse, after all! It is all a plot by those Tang Clan bastards! Aren't they just impersonating the Grand Prince's flag to buy time?"

A middle-aged man with a clean, handsome face and notably thick eyebrows giving an honest impression prostrated himself.

He was too handsome to be called Chuanglan Jinhu\footnote{瘡爛 金狐. Changnan Gumho (창난금호) in the original text}. 

Chuang meant bedsore, and Lan meant a burnt, festering wound, so it was a name that implied an ugly fox-like beast (Jinhu). 

Chuanglan Jinhu poured out his indignation with his whole body.

His face was contorted and trembling, his eyes filled with tears of anger and injustice about to spill over.

His reddened ears and bulging veins were the appearance of someone clearly wronged.

And the Imperial Censor felt convinced by this.

"However, no matter how outrageous these traitors are, how could they dare impersonate the Grand Prince's flag? If something goes wrong…"

The Emperor was an indifferent person.

If something unfortunate happened during a mission, it wasn't the Emperor's order but the incompetence of the one who received the order.

At this rate, they would be traitors whether they gave up on the Tang Clan or pushed forward.

So the Imperial Censor finally turned the arrow to the one who had brought about this mess.

"That… Elder Eunuch. What should we do now… We bombarded the Tang Clan as instructed, but is it alright for this humble one to continue carrying out the imperial order like this?"

The Imperial Censor looked for guidance.

One might ask, why was the highest-ranking official and person in charge now speaking respectfully and looking for guidance from someone else?

Upon this, a soldier who had been on duty keeping the fire and boiling water in a corner of the tent naturally answered.

"Since when did I recommend bombardment? I merely advised that since something that absolutely should not have entered had gone in, you should either retrieve it or eliminate all witnesses, did I not?"

It was an affected voice, unnaturally nasal as if forcing it through the nose, though not a woman's.

"But Elder Eunuch, you…"

"Since you've already done it, wouldn't it be better to complete the task and then beg for forgiveness? Just push through as you've been doing. Even if the Grand Prince is inside, people only die once in their lifetime, don't they? Someone who has already passed away cannot die twice, can they?"

It was an incredibly outrageous statement.

To think he would suggest to push through even with the Grand Prince inside and pretend nothing happened.

Chuanglan Jinhu's eyes flashed.

If this quasi-woman with an affected voice, this eunuch, was called Elder Eunuch and was a high-ranking official, there was no need to think about their identity.

\textit{Eunuch fucker! It's a bastard from the Eastern Depot!}

In that instant, Chuanglan Jinhu sprang up and swung something from his bosom, splashing a sticky liquid onto the Eastern Depot bastard's face.

"Kyaak, what, what is this!"

"Haha. I wondered why a eunuch of the Eastern Depot wasn't involved in this fishy business. It did smell like the thoroughly rotten discharge of someone with Imchang, you bastard. If you don't wash your face properly, you won't escape great trouble!"

Imchang\footnote{Syphilis} was a type of venereal disease.

When severe, it was a serious illness that could cause flesh to rot and fester.

The thoroughly rotten discharge of someone with Imchang.

Understanding the meaning, the Eastern Depot eunuch's pupils shrank, his mouth gaped open, and he immediately let out a terrible scream.

"Kyaaaak!!!"

"Haha, serves you right!"

"You, you bastard!"

The Imperial Censor hurriedly drew his sword.

However, Chuanglan Jinhu had already positioned himself near the entrance.

"Looking at the Imperial Censor's face, I thought your guts were only as big as mouse piss and your temperament softer than tofu. As such, you didn't seem like the material to plot such a terrible scheme. But lo and behold. With that incompetent nature, how much dirty money did you have to offer to become an Imperial Censor?"

"You bastard!"

"You fired artillery at the place where His Highness is, so your life and the lives of your entire family end here! Go ahead and struggle all you want!"

With that, he immediately fled using Qinggong, slipping away on all fours like a running dog.

The eunuch was too busy screaming, crying, and wiping his face.

Meanwhile, the Imperial Censor felt greatly dismayed.

It was now all or nothing.

As the eunuch had said, it was better to complete the task and beg for forgiveness than to give up and return.

The Imperial Censor shouted as he left the tent.

"Sound the drums! Advance and sweep away all those traitors!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A fox crawling on all fours quietly appeared before the eccentrics of the royal household.

Hag Yan, with her rotating Chakra Demonic Eyes narrowed, spoke in a suppressed voice.

"Well, look who it is. Isn't it the traitor fox?"

"Hehe. Old Hag. A traitor? What a hurtful thing to say."

"Are you denying it? Didn't you put poison in His Highness's tea cup?"

Chuanglan Jinhu replied smoothly.

"Someone offered me gold and asked, so I just obliged. You know my nature is too soft to refuse requests."

"If you do not answer properly, know that today will be your death anniversary, you little fox."

"No, Old Hag. Do you think I didn't know His Highness was away when I put in the poison? If it wasn't me who did it, they would have kept trying with others until it worked. As such, if trouble was bound to happen anyway, shouldn't we have one traitor die and find out who was plotting?"

"How can I trust the words of a con artist? So who was it?"

"I thoroughly smeared the Eastern Depot bastard with Tracking Scent."

Tracking Scent was a type of special fragrance; a substance applied to allow trained animals or trackers skilled in special Qinggong to track targets.

Hag Yan snorted at this.

"Hmph. Fox, we'll deal with you later. Old Dog?"

"No need to tell me, I'm going. Just keep an eye on this fox bastard."

Old Dog sniffed the air, looked in one direction, and then leaped away, disappearing.

Only then did Chuanglan Jinhu quietly ask a question.

"But Old Hag, why are you all suddenly gathered? Why a night walk? With guys who never left the royal household before, at that?"

Hag Yan answered with a white smile.

"We're going to screw over those Embroidered Uniform Guard bastards. What about it?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Imperial Guards were elite soldiers directly under the Emperor; from the start, they were on a different level from the local government troops.

From monthly wages to support for martial arts, they were truly the Emperor's soldiers, naturally different from those local country bumpkins who were just cannon fodder for wars.

So there were the real soldiers, the Imperial Guard, and below them were the local country bumpkins.

Of course, this was what the Imperial Guard claimed.

To the Sichuan soldiers, however, the Imperial Guard were just annoying uncles who put on airs.

So even after hearing the secretly passed down orders, they just thought, 'Wow, those annoying bastards who always have their noses up all high must have really messed up'.

At the sound of drums signaling the advance, the Imperial Guard first gathered among themselves to wait.

There was no need to go first and become human guinea pigs for the veritable obstacle course within the impregnable fortress of the Sichuan Tang Clan with all its traps.

After all, wasn't this Sichuan's business in the first place?

Such expendable missions were for the Sichuan soldiers to do.

So they gathered quietly, saying you guys go first, we'll charge in later and gain military merit.

While watching the General's Cannon approaching, pulled by grunting soldiers in front and pushed with difficulty from the sides and back, they just snickered saying, ‘You guys are working so hard. Won't you get all wet in your breaches at this point?'

This General's Cannon, which typically existed in quantities of two per thousand-man unit in general military formations, was a primitive shotgun that fired by filling it with gunpowder and pouring metal fragments and stones on top to shoot at the enemy in front.

The Imperial Guard's mockery didn't last long, because the muzzle of the General's Cannon that had been brought with such difficulty was, for some reason, pointed at them.

In the moment they went 'Huh?', someone lit the short fuse with a flame stick, and before they could even take a few steps back shouting "Dodge!", the cannon roared, tearing people apart.

Following that, Fire Lance Troops holding Fire Lances formed a wall of flames, and arrows rained down above it.

The Imperial Guard, unable to even form a formation, became entangled in chaos and pandemonium.

For reference, the Fire Lance was a weapon that was a rough equivalent to an ancient primitive flamethrower, created much earlier than cannons.

The tactic of people suddenly charging in to fight in close combat was an outdated doctrine used in ancient times when Liu Bei and Cao Cao1 were contending for all under the heavens, and Sun Quan2, a local strongman, was causing trouble in between.

Why would martial artists who could break rocks with their bare hands and easily leap over city walls fear the government's soldiers?

A mere local gangster organization couldn't possibly stand against soldiers armed with cutting-edge primitive firearms.

However, since a war between the government and Wulin was obviously mutually assured destruction, they just pretended not to see each other, elegantly expressing it as the non-interference between Wulin and the government.

Of course, the result would be considered a win in terms of points for Wulin.

If the two fought, the dynasty would certainly fall, leading to the revival of the Sixteen Kingdoms or the Warring States period, but Wulin's lineage would somehow remain and continue.

At any rate, these were the horrific scenes unfolding outside the Tang Clan while Qing was asleep.
