\chapter{Tang Clan's Paper Flower (8)}

The dogshit, or rather catshit, that was spoken had reached a level that transcended shamelessness, so even the Imperial Censor's brain functions temporarily stopped, leaving him in a daze.

Then he suddenly shouted.

"How can that make any sense?!"

"We find it hard to believe too. But what can we do if it's the truth? Should we lie because you might not believe it?"

"Is your face made of Cold Iron? It seems you are someone that is impossible to communicate with. Well, I shall have to verify if what you say is indeed true. You there. Go in and prove your Clan Lord's words."

At this, one of the Tang Clan experts who was pointed at showed his palm and answered.

"Do you mean me? This unworthy one believes in our Clan Lord, though."

"I did not ask whether you believe him or not. I said to prove it."

"If that is what you mean, I saw that cat clearly with my own eyes, so there is no need to worry."

The Imperial Censor realized that pressuring them any further would be futile.

But if he immediately sent soldiers rushing into the Tang Center, they would clearly seize the opportunity to spray the prepared poisons.

At this, the Imperial Censor gritted his teeth.

Qing's eyes lit up as she saw this.

She then took two steps to the side and quietly asked an old man who had been introduced as some high-ranking elder.

"Excuse me, were we allowed to provoke them from our side? You said earlier that we had to endure great humiliation."

"'Our side', you say. Ah'er has truly made a good friend. How admirable. Here, I'll give you this."

"Ah, thank you."

The old man very naturally took something out from his bosom and handed it over.

It was a small medicine bottle about two finger joints in size.

"It is a personally modified version of the Soul-Dragging Water. If there's someone you dislike, mix it in sweet alcohol and make them drink it. After one quarter of an hour, their muscles will relax and they'll soil themselves with excrement and urine."

It was truly a deadly poison that could destroy someone's social status in one go.

"Wow! Thank you! Such a precious thing."

Qing brightly smiled as she pocketed the special Soul-Dragging Water.

Because Qing's expression was extremely honest, the old man's face also broke into a smile upon seeing her pure joy.

\textit{But who is this elder? Is he some poison vending machine?}

\textit{Is this like those village people in games who give you an item when you talk to them?}

The answer was that he was the Grand Clan Lord, the highest-ranking elder of the Tang Clan, who was sticking close by out of worry for his granddaughter.

He was also the one responsible for getting Tang Lan-ah interested in all sorts of vicious poisons by giving her gifts since childhood.

The Grand Clan Lord then added an explanation.

"The Tang Clan does not forget grudges, so the insolence of kicking open the main gate of the Sichuan Tang Clan is a serious crime that should be punished by death. Just enduring that is humiliating enough, so shouldn't we at least irritate them a bit?"

"Ah."

"However, it would be even better if they make a big verbal mistake. Isn't it the way of Zhongyuan that we can use our swords if we find justification by picking at their words?"

There has never been such a way in the world from ancient times to now.

But the rule of the world found by an old man who had lived long wasn't wrong either.

"However, if one of us makes a mistake, we'll all be annihilated, while if one of them dies, another will just replace them. So it's an extremely disadvantageous fight for our Tang Clan. Do you understand?"

\textit{What? So we can provoke them from our side?}

\textit{Then, isn't that my specialty?}

Qing's eyes sparkled brightly.

"Then, can I join in provoking them too?"

"That desire to help in any way is truly lovely. How admirable. Here, I'll give you this. It's a personally modified version of the Soul-Seizing Oblivion."

The Grand Clan Lord handed over another small glass bottle.

Inside were three pills that looked like goat droppings.

"If you make them swallow it by shoving it into their mouth, after the medicine takes effect, it will stimulate their lust while making them see hallucinations. You'll definitely be able to see them humping the air… Oh my. I shouldn't say such things to a young lady. How thoughtless of me."

"Wow! Thank you! It sounds fun, so I'll definitely use it."

It was another deadly poison that would bring about death to one's social status.

She wasn't sure what he kept personally modifying, but since it was precious, Qing happily accepted it again.

"However, Touzhong, that fellow. Didn't he secure the Clan Lord position because he was originally incredibly glib? There's no one in our family who can wag their tongue better than him, so if we leave it to him, he'll handle it well on his own."

Sure enough, after that, the Regional Military Commissioner had no choice but to withdraw.

"Ahem. It seems the search is not feasible, so we will withdraw for today. Quickly deal with the poison and comply with His Imperial Majesty's august command."

It was a win on points for the Tang Clan.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Imperial Censor didn't come just to be pushed around, so the next thing he did was to blockade the Tang Center.

By surrounding it with soldiers and blocking all entrances and exits of the Tang Center, he prevented not only people but also supplies from entering.

Among the supplies was food, and since people couldn't live without eating, it meant they should either starve to death or die for treason.

However, Qing ate well.

The Tang Clan members also ate well.

This was because there were already several secret passages. As such, all that really changed was that it became just a bit troublesome to bring in supplies.

Since what the Tang Clan needed was time, they also pretended to meekly endure.

"Oh my, good men. If you block even our food supplies, how are we supposed to live?"

"Ahem, ahem. We're just following orders too."

It was like this.

By the fourth day, even the Imperial Censor started to feel something was suspicious.

\textit{Wasn't this a bit strange? Did they really stock up on that much food?}

Meanwhile, two points had been marked on the map of Sichuan, meaning they had already found the locations of two artillery positions.

It was only on the seventh day and night that the Imperial Censor finally realized something was amiss and rushed back with a horde of soldiers.

This time, he not only came himself but also brought new members: a group of martial artists dressed in martial attire made of brilliant golden silk.

"I clearly warned you, yet you still have not taken on the appearance of criminals."

"Criminals? Where are there any criminals here?"

"Hmph, Guard Assistant Commander. What did I tell you? Look at the shameless lies of these outrageous traitors. We should immediately rush in and slaughter them."

Qing watched this scene and asked.

"Who are those sparkling guys?"

"They're called the Embroidered Uniform Guards."

The Embroidered Uniform Guards, also known as Golden Uniform Guards, were literally guards wearing golden clothes.

However, since this golden martial attire was the exclusive uniform of the Emperor's direct military group, each and every one of them held quite high official positions.

They were almost identical to the group called the Life Guard when Germany was an empire back in Qing's homeworld.

They were the army, secret police, and the Emperor's blade all in one.

The complexion of the Poison Grandfather, no, the Grand Clan Lord explaining this, darkened a bit.

"It seems the Emperor has made up his mind. A Guard Assistant Commander is the third highest position in the Embroidered Uniform Guards, so they rarely come down to the provinces under normal circumstances."

At any rate, another war of words betting the family's fate was about to begin.

"Seven days have passed, so you must have surely detoxified by now. This time, you should accept the sear-"

"Oh dear. In truth, last night, a mischievous wild cat caused havoc in the warehouse, and unfortunately, it ran around with a pouch of deadly poison in its mouth, turning the entire Tang Center into a trap no different from an area of death."

It was exactly the same line, as if it had been copied and pasted.

"Did you not say the same thing last time?"

"Isn't it said that history often repeats itself?"

"T-There should be a limit to shamelessness, even if…"

The Imperial Censor trembled with a disgusted expression.

Meanwhile, Qing just admired such a scene.

\textit{Isn't this an incredible second rendition? Basically like a meme?}

Furthermore, it was a declaration of intent to thoroughly milk this for three or four more renditions. They seemed to be ready to reach the realm of internet comments; all yap and no logic.

It meant that every night before they came to visit, an invincible cat with immunity to all poisons would steal an infinite pouch of poison and meticulously spray it all over the Tang Center.

However, the Imperial Censor was no ordinary person either, so he immediately realized that there was no way forward in this standoff and turned to leave right away.

At that moment, Qing suddenly raised her voice.

"Oh right! Imperial Censor! Just a moment! I have something urgent to tell you."

The Imperial Censor, who was about to take a step, looked at Qing's veiled face with a dubious, yet somewhat expectant gaze.

"…What is it? If you're going to report these outrageous traitors, I swear on my name that I'll do my utmost to save you alone, Woman."

Then Qing turned to Tang Touzhong and spoke.

"Well about that… Clan Lord? Our food waste is overflowing and it's been smelling a lot lately. Couldn't we ask them to clean it up on their way back? They're the ones who blocked us and prevented us from coming and going, so shouldn't the ones who blocked us clean it up?"

"Ooh. That is indeed a good idea. Imperial Censor, may I make an earnest request? Our chef makes such huge portions that the Tang Clan members usually have more than enough to eat with plenty left over."

It was a taunt saying that no matter how much they blockaded, it was useless because they had separate ways to bring things in.

Some Tang Clan members deliberately responded with giggling laughter.

"Shut up, you traitors who are not even worth associating with! You should be torn limb from limb and thrown to the dogs! You should be skewered and roasted to feed to your own children!"

"Ah. You wish to talk about the end of traitors? Then how about using those whose belly fat we stick wicks in to use as candles? The Imperial Censor alone should burn for a good seven days."

It was a refined jab at the Imperial Censor's Dong Zhuo-like physique.

"Y-You…! Let's go! These fucking sons of bitches…"

In the end, the Imperial Censor, with a face turned bright red, left while cursing.

Sichuan Tang Clan: Victory No. 2.

After that, Poison Grandfather held out another glass bottle.

"The child's quick wit is truly admirable. How praiseworthy. Here, I'll give you this. It's a personally modified version of the Immortal Waste."

This time it was an empty, sealed glass bottle.

"If you make them inhale it through their nose or mouth, for fifteen days their breathing will change to sound like an ugly flute, making them wheeze roughly. On top of that, their voice will change to be even more ridiculous, so they won't be able to hold back their laughter even at their own words. If there is someone who laughs easily, they might even laugh so much they suffocate."

Every single thing he touched was consistently a poison aimed at ruining someone's reputation.

"Wow! Thank you so much. I wasn't expecting this, but hehe. I'll use it well."

Qing happily accepted the bottle once again.