\chapter{Tang Clan's Paper Flower (16)}

\textit{Ooooh, a Grand Prince. That's pretty cool.}

That was Qing's impression.

In truth, Ziyou hadn't tried to hide that he was the son of a well-off family.

Qing hadn't particularly cared about it either.

It was like an unspoken agreement to pretend not to know, so Qing didn't think she had done anything particularly wrong.

The unfamiliarity with the Grand Prince system also played a part.

When people of Korean descent thought of rulers in this medieval Wulin, wouldn't they just go 'Wow, an Emperor!' and be done with it?

They wouldn't know much about various royal prefectures, or that they could be the actual rulers of a region, or that they could command all the military forces of a province, or that they occupied the first place in the hierarchy of princes, generals, and ministers below the Son of Heaven.

This was because no ethnic group in the world was actually curious about medieval China.

Even the Chinese descendants weren't curious. After all, they burned that history, so it would honestly be stranger for someone to know about it.

There was only a bit of demand for ancient China when Liu Bei and his brothers were running around.

(And even that wouldn't be possible without the medium of comics)

So Qing's reaction was lukewarm.

"Uh, um. Your Highness Grand Prince? What should I call y-"

"How dare you! Will you not show proper respect!"

\textit{Shit. Why does this one keep yapping? Who does she think she is?}

Qing shot a glare at the noisy woman and then looked back at Ziyou, Grand Prince Dexian.

"Call me Your Highness."

"Ah. Your Highness. But what's this? Why did you pretend to be dead? Or wait no… Wasn't it when we were eating together that we heard the news?"

"No, you wench! You must refer to him as Your Highness! You should be prostrating yourself with your clothes properly arranged, and even that wouldn't be enough! Do you think you can rely on some small acquaintance you had with His Highness?"

The woman foamed at the mouth again.

However, listening to it, there was some reason to her words.

Come to think of it, even if a king came out to dally around, hiding his identity, because he was bored, just because you became a bit close at that time didn't mean you remained friends.

If one had to make a comparison, it would be like the heir of a chaebol family who came as a new production worker for a brief change of pace.

How ridiculous and pathetic would the bizarre production worker culture of auto-hunting games, self-breaks, and company-paid dinners seem?

Thinking about it that way, Qing also felt upset.

\textit{Did he think that if he suddenly went 'Ta-da, I was a Grand Prince', I would applaud, saying 'Woahhh, that's so awesome'?}

\textit{Did I look like a materialist who would rush over wondering if there were any crumbs to be had from his money and power?}

A proper person, even if their identity was revealed, should properly sort out the relationship, saying something like 'Due to circumstances, it ended up like this, but I'm still grateful for everything', or 'I'd like to remain friends'.

Moreover, the Prince didn't particularly stop the woman.

Usually, when someone was of high status, they let others say the unpleasant things they didn't want to say themselves.

Qing immediately corrected her crooked posture.

As if she suddenly had two personalities, she immediately took on a gentle and demure appearance.

"This humble fairy lacks knowledge and has committed rudeness towards Your Highness. Since it was done in ignorance, would you generously forgive me?"

"I came out in plain clothes, so it is natural that you did not know. There is no need to mind it, so you need not worry about that."

"Yes. Thank you for everything until now, Your Highness."

"No. Ahem. Ahem."

Grand Prince Dexian looked at the woman with a flustered expression.

The woman also seemed flustered.

Because 'Thank you for everything' usually meant the end of a relationship.

"Ahem. Spear Woman."

Spear Woman felt dismayed.

It was Spear Woman who had insisted on verifying Qing.

Old Dog didn't have many days left to live, so he would make a fuss even if just one girl stuck close to His Highness, saying things like "serving the little master" and whatnot. However, that wasn't the opinion of all the servants in the royal household.

From what Spear Woman had heard, she was a woman who just wagged her tail at the son of a powerful family.

She thought that once His Highness revealed his identity, she would surely pretend to be close and aim for the position of a consort.

Well, that was the kind of verification it was.

Meanwhile, Qing was in a state of shock.

\textit{No way, how can a person's name be Spear Woman?}

\textit{And for a woman at that!}

\textit{It can't be, right? It must be some kind of title, right?}

\textit{No wait, Spear Woman kinda sounds like Slut Person1! How can a person's title be Spear Woman? Or even Slut Person!}

\textit{And for a woman at that!}

At that moment, the unfortunate woman with both a pitiful name and title, Spear Woman, spoke with a much softened attitude, seemingly embarrassed.

"Ah, ahem. Um. You said you were Young Lady Ximen, right? How can one cut off human relationships so coldly?"

"Isn't forcibly holding onto a relationship that isn't meant to be just seen as pathetic begging? Rather than that, it is better to just have one thing to brag about, saying I was once called a friend by His Highness in the past."

"No, that is… It doesn't have to be just in the past."

"Forget it. Tell him to speak for himself if he has something to say. What's with setting up a spokesperson to embarrass people? Does he think a woman who grew up poor will go crazy and rush over just because he's a high-ranking person?"

At this, the Tang Clan people who were listening turned pale.

While Qing's rough comparison of a chaebol son and a Grand Prince might fit to some extent, there was no such thing as a perfect analogy in the world.

There had never been such blasphemy; the Grand Prince they saw as a lifeline turned out to be a potential fuse.

"That… I am sorry. I did not mean it that way. I did not deliberately hide it, so please do not be angry."

The Tang Clan people who were anxiously spectating eventually let out a sigh again.

'He's actually apologizing so readily!'

"If it wasn't deliberate, why did you remain silent until the situation reached this point? Couldn't this whole mess have been avoided if Your Highness had just said one word that you were alive?"

"Well, I too heard the news that I had passed away. When the person in charge during my absence collapsed, I too needed time to figure things out…"

Qing narrowed her eyes.

Ziyou broke out in a cold sweat and suddenly thought.

\textit{But why am I acting like a criminal?}

"Ahem, I am a Grand Prince."

"Yes, Your Highness Grand Prince. And this is the Tang Clan underground that's been hit by artillery fire. It looked absolutely fucking destroyed."

Ahem. The Tang Clan Lord cleared his throat uncomfortably and muttered 'It's not absolutely fucking destroyed…'

"…Please do not see me as too cold-blooded."

Ziyou shrank again.

At this, the Tang Clan people thought.

'He's completely cuffed. There is no doubt about it.'

'He's cuffed so tightly that he's being swung around.'

Feeling their gazes, Ziyou made an embarrassed expression.

"Um. Well. That. We should move to a different place."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Emperor hated Wulin.

The hatred passed down since the Celestial Martial Emperor had already crossed the line of common sense; to the point where he would pass the throne to the child who hates Wulin the most.

No matter how strong Wulin Practitioners were, unless they were giants reaching the heavens like the Celestial Martial Emperor, they couldn't survive against hundreds of thousands of elite troops.

It was not like soldiers didn't practice martial arts.

And a Master's Inner Qi isn't infinite either.

When True Qi was depleted, they were just a tough, good fighter at best, so if they just overwhelmed them with sheer numbers, even though the casualties would be high, there was nothing that they couldn't push back.

However, if the casualties were that high, what was the point? Wulin hate or not, the imperial dynasty would change afterward, so they couldn't recklessly charge in.

So it seemed they thought that while keeping an eye on the situation, if they were going to remove one, it would be better to erase the most dangerous one.

And that was the Sichuan Tang Clan.

Because they had biochemical weapons that could overwhelmingly increase the exchange ratio of martial artists to soldiers.

"I was wondering why Elder Brother sent me to Sichuan. But it makes sense. This too is an ancient capital where a king lies, after all."

The wise assume the worst.

The Dexian Royalty was established about ten years ago, so if they had been dreaming of dealing with the Tang Clan after the assassination since then, it would inevitably be dangerous to reveal oneself carelessly.

"I thought I had conducted myself well to avoid falling out of favor, but it seems he still intends to eliminate me."

So he acted as if he didn't exist at all.

Even the good king praised by the people was actually an illusion.

It was just that he didn't accumulate wealth to avoid being bothersome. As such, all he did was buy grain and throw it to the poor.

Because he put his own people in key government positions instead of the Emperor's officials, there was an uproar about driving out corrupt officials.

It wasn't ruling by the virtue of not ruling, but just not showing his face out of fear of the Emperor.

"But well, then. It couldn't be helped, huh. If it was to survive. But why are you here?"

"With this opportunity, we might be able to take control of Sichuan by cooperating with the Tang Clan. If Sichuan's government and Wulin join forces, even His Imperial Majesty would have no answer. However."

"However?"

The Grand Prince straightened his posture.

As he did so, there was a natural dignity emanating from him despite not having learned any martial arts.

Qing felt anew that perhaps not just anyone could be a king.

"Is there any need for Wulin to exist? His Imperial Majesty rules the earth with the legitimate authority received from Heaven as the Son of Heaven. In this vast land, his stern laws come from him, yet dare these sword-carrying groups act as if they are the masters of the land and exploit the common people?"

Grand Prince Dexian siding with the Sichuan Tang Clan was not something to be taken lightly.

The Emperor had already sent the Imperial Censor and Embroidered Uniform Guards to erase the Tang Clan, so the Grand Prince opposing and confronting that would be seen as rebellion.

After that, it would truly become treason.

Of course, the Emperor had tried to kill the Grand Prince.

But wasn't the Emperor someone who had the authority to order the death of his subjects?

So Grand Prince Dexian's question wasn't just out of curiosity, asking for an opinion.

It was because the Grand Prince had been unable to come to a conclusion after pondering alone for so long.

Whether it was okay to acknowledge that Wulin was necessary for the world and share the authority to rule.

It was the final question about an irreversible decision, asking whether the Grand Prince of Sichuan should help a mere Wulin sect and raise a sword against the Imperial Family.

And so Qing answered.

"Why are you asking me that?"

Ziyou frowned deeply.

"Hmm. Didn't it feel like I was asking something extremely important? You, no. Friend, you also helped the Tang Clan, so haven't you fulfilled your duty as a member of Wulin? So I'm asking you, a Wulin Practitioner who is my friend, not my subject."

"What do you mean, a member of Wulin? I just helped because I thought the Tang Clan members were good people. They provided free medical treatment and had a good reputation, didn't they?"

"Provide? Wasn't it just them trying to develop their medical skills? It's just that the results were good while pursuing their own interests, so does that make it a good thing?"

Qing chuckled and spoke.

"If the results are good, that's enough, isn't it? Anyway, isn't it a good thing if others like it? In my opinion, the Tang Clan acting as free doctors is much more beneficial to the world than an Emperor with only a bad reputation."

