\chapter{Tang Clan's Paper Flower (4)}

"I see. It was the Rotting Flying Fox. I didn't see him that way."

Ziyou nodded.

His voice was filled with calm regret.

"Your Highness, just say the word. I'll immediately bring that thick-faced con artist to his knees before you. Ah, of course, I do not mean me. These old dogs here will. Combat is not my specialty, after all."

"That's enough for now. He might have had his reasons. It's not too late to interrogate him after knowing the full details. Doesn't everyone have circumstances they couldn't speak of?"

"Oh my. Your Highness is too soft. Originally, traitors should be torn apart to set an example."

As Hag Yan said this, her eyes flashed strangely.

Three tailed wisps of soulful fire seemed to dwell in her pupils, slowly rotating.

If Qing had seen it, she would have been unable to contain her admiration with incomprehensible words like "Woah, sperm eyes! It's like HotS!\footnote{The stylized 'o' in the 'Heroes of the Storm' logo}"

And if it were a Wulin practitioner other than Qing, they would be shocked for a different reason.

It was the Chakra Eyes of the Chakra Witch who had thoroughly wiped out the Yuncheng Sect thirty years ago and disappeared.

It was a characteristic of the Chakra Demonic Tribulation \footnote{Jeonryunmageob (겁전륜마겁) in the original text. 'Jeonryun' or 'wheel turning' refers to the concept of chakra}, one of the Ten Great Demonic Arts under Heaven.

"That's enough. When I first accepted that fellow, didn't I say that his nature as a con artist meant he wouldn't be able to endure forever? I answered that if that was the case, he should stay until then and leave. It seems he thought it was time to leave now."

"Your Highness… How can your heart be so noble?"

Hag Yan sniffled and wiped her eyes.

Originally, the grudges and favors of Zhongyuan were like a vast and deep ocean; as one advanced with a sword, they would sink deep into it.

When one looks at the world after sinking like that, the grand beauty seen from outside the water has long since disappeared.

Only the desolate scenery of the dark and damp deep sea is reflected.

It was because the grudges and favors of Wulin are merely an accumulation of resentment.

Favor would eventually become someone else's grudge.

Humans were creatures that easily forgot favors and firmly engraved grudges.

In the end, only grudges remain, so the place where Wulin practitioners eventually reached was a swamp of resentment that clung stickily to the body.

So some who lost their purpose in Wulin buried themselves in remote mountain valleys, while others threw away their swords and acted out the lives of ordinary people. But in most cases, the end was bitter and left a bad aftertaste.

However, a very lucky few sometimes meet good people when they despair of the world and receive salvation.

Grand Prince Dexian was one of those people.

He was a great man who willingly accepted those who were tired of the world, those who couldn't bear their grudges, those who lost everything while being chased by false accusations, or even those who were actual Demonic Adepts, and brought them into his fold as family.

Ziyou smiled bitterly.

"Would a person with such a kind heart just watch this situation while only worrying about the safety of his family?"

Silence lingered for a moment.

Then the youngest voice among them asked.

"Then, shouldn't you start preserving your precious jade body soon?"

It was a way of urging that they should leave the Tang Clan, now that they had caught the rat in the royal prefecture.

Ziyou pondered with a complicated expression, and finally, as if he had made a decision, opened his mouth.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Last night, Old Dog stopped by to inform that they would be leaving.

And the next day, Peng Chaolei left.

"Is Young Lady Peng leaving too?"

"There's no choice, is there? If the eldest daughter of the Hebei Peng Clan gets caught up in treason, how would I be able to face the Elders?"

The Hebei Peng Clan was in Hebei.

And Beijing was also in Hebei.

Just as the Kunlun Sect were the ones to get crushed first when the Demonic Cult rampaged, the Peng Clan would bleed heavily when the Imperial Family draws its sword.

So the Peng Clan had a principle of never antagonizing the government.

"I'll give you the dadao as a gift, so keep training with it."

"Hmm. I wonder if Gramps will be able to carry it."

Although Cui Liweng was a Master in the Unrestrained Realm, he was emptying his dantian and building it up from scratch because he was switching to a completely different Buddhist Divine Art.

Qing had also greatly worried about whether she could pass on the Great Meditation Art to a Great Demonic Adept, but it was an unavoidable choice after granting Gramps the special privilege of being able to take care of her.

It was for the sake of Gramps' mental health, as Qing had directly experienced the mental protection performance of the Great Meditation Art.

What if Cui Liweng, who already showed signs of dementia, went completely crazy?

Whether it was effective or not, Gramps' expression was gradually changing to resemble a benevolent Buddha.

He had even started to gain a little weight, to the point where his previous appearance as a hollow-eyed skeleton could no longer be seen.

Peng Chaolei burst into laughter at that muttering.

"You should carry that much. You're strong enough."

"Wait what? That makes it seem like I'm passing it off or something. Gramps is the one taking it away, you know?"

"Right. But it is difficult to say that is the case. Aren't you a bit too casual about going along with it?"

"If I'm uncomfortable when he's doing it to make me comfortable, what's the use? So I need to be comfortable for Gramps to feel rewarded."

Cui Liweng nodded in agreement.

And so, Ximen Qing acquired the Hell Sword (No. 3)!

Peng Chaolei laughed again at this sight and then continued.

"That child Lan-ah seems to have been quite shocked. Since you decided to stay, try to take care of her. It seems she hasn't realized the heartlessness of Wulin yet. Because Wulin has only been kind to Lan-ah so far. Do you understand what I mean?"

"…?"

Qing answered with her expression.

At this, Peng Chaolei answered by fluttering her hand in front of her face a few times like a fan.

Then, with a light attitude without a trace of lingering attachment, she turned her body and strode away.

After seeing her off and returning, Qing found Tang Lan-ah sitting on the porch of the guest hall, swinging her legs with nothing to do.

"Aren't you seeing patients today?"

"There are no patients…"

Tang Lan-ah answered in a gloomy voice.

Even the Tang Clan Clinic had suddenly lost its patients.

Only a few people who were really seriously ill or on the verge of death visited, while others thought they'd rather just be sick than risk being implicated in treason.

With slumped shoulders, she swung her feet back and forth, then casually asked.

"What about Sister? Did she leave?"

"Well, since it's a matter where her clan is on the line, Young Lady Peng had no choice."

"Mm."

It seemed like she mumbled something like 'Our clan is on the line too', but it wasn't clear.

Then she asked again.

"Then what about you? Aren't you leaving? You're a disciple of the Divine Maiden Sect."

"I'm just an Outer Disciple anyway. I don't even have a name registered, hehe."

Qing wasn't listed in the Divine Maiden Sect's register.

It was Ximen Surin's warm consideration.

If the Divine Maiden Sect ever got in the way of her disciple's chosen path, she was prepared to expel her at any time. As such, she was allowing Qing to just follow where her heart leads.

After all, expelling an Outer Disciple who wasn't even registered would only change her title.

And even that would just be revoking her Divine Maiden Sect discipleship, not telling her to quit being a named disciple, so she should just do as she pleased.

"And this Ximen Qing can be called a man among men. Without loyalty I am nothing but a corpse."

Actually, she was pretty close to a corpse even with loyalty.

But Qing didn't know. There were only two people in the world who knew about this, one in this world and one in the afterworld.

"What's that even supposed to mean? How dumb."

Tang Lan-ah said this, but a smile slowly spread across her face.

Then she hopped up and stood on the ground.

"Well. There are plenty of those who can't even be called men. Hmph. They did say about how ‘The storm put strong grass to the test'. I've changed my opinion of you."

"The storm put strong grass to the test" was roughly similar to the Western proverb "A friend in need is a friend indeed."

It was praise given by Emperor Guangwu, an incomparably great Sage King among human emperors, to Wang Ba who alone remained and kept his position during difficult times in the Warlord Era.

Afterwards, Emperor Guangwu also kept his loyalty to Wang Ba and made him the Grand Noble of the First Clan Under Heaven.

Instead of using 'A long road tests a horse's strength', which had the same meaning and was used for friendship, she deliberately used 'The storm put strong grass to the test', which spoke of the loyalty and integrity of subordinates. This was fitting for an arrogant and wicked woman like Tang Lan-ah.

Of course, Qing didn't know any of this, so she had no thoughts about it.

"What's there to change your opinion about?"

"That… Do you want to go look at hidden weapons?"

"So suddenly?"

"Uh, you know, um. So. Ah. Right. You blocked that needle tube with your hand last time, right? You do such things because you don't know what's dangerous. If we look at them now, maybe you'll know what's dangerous later."

Indeed, it was logical persuasion worthy of a doctor of traditional medicine.

Qing was good at spouting nonsense but weak against logic, so in the end, she was convinced.

Moreover, it was also a matter related to survival.

"That makes sense. Let's go right now."

And so, the Tang Clan's secret storage of hidden weapons was opened wide.

In fact, hidden weapons lose much of their power just by knowing about them and being prepared in advance.

That was why it was the essence of the Tang Clan. One that even branch family members couldn't enter unless they reached a certain level of achievement, let alone outsiders, to prevent leaks.

Yet, she opened up that storage completely out of a desire to get close.

It was a treacherous way of building friendship that only a terrifying and wicked woman who didn't discriminate in her methods could do.

If the Elders of the Tang Clan found out about this?

Well, they would say it can't be helped if it's for a friend.

Because everyone already knew and worried about the fact that Tang Lan-ah had no friends.

This essentially proved Tang Lan-ah how meticulous her scheming was, and one could say she was indeed not lacking in making a name for herself as one of the most wicked women under the heavens.

Thanks to this, Qing properly expanded her knowledge of hidden weapons.

Qing didn't know that so many hidden weapons existed in the world.

She thought it would just be throwing knives or that bamboo tube from before, but that wasn't the case.

Just from what she saw, there were already Sa and Sa and Sa, needles and needle tubes, wang and zhili, penny whistles. Shi and zhen, di, xiao, and all sorts of shaped throwing weapons…

Tang Lan-ah excitedly explained.

Sa (砂) was sand, usually soaked in poison and thrown at the face with special techniques or gloved hands.

"It's best if it gets into the eyes, nose, and mouth, but Masters can block it. So sprinkling it in the hair is most effective. Poisonous sand that burrows into the hair doesn't come out easily. Plus, it can cause hair loss due to the poison. Hehehe."

Qing shuddered at these terrifying words.

\textit{This time, she really seemed like a villainess.}

Sa (梭) was a weight with a thread attached. It could be used to set traps with poisoned thread or thrown like a meteor hammer to make contact with the body.

Qing shuddered at this point.

\textit{I really hate threads…}

Sa (射) referred to arrows, hidden weapons shot with special bows disguised as folding mechanisms or musical instruments.

Needles were the needles everyone knew, and needle tubes usually refer to mechanical devices that fire needles.

Wang (網) was a net.

Qing shuddered again at this point.

\textit{I really hate nets too…}

Zhili (蒺藜) is a general term for hidden weapons spread on the ground to target the soles of feet.

They come in various shapes from simple tripods to flat ones that don't rise up, reminding Qing of an object from her homeland.

They looked like those foot mines disguised as toys that children assemble and adults collect.

Shi (矢) referred to arrows shot from bows, and special ones included fire arrows coated with white phosphorus, yellow phosphorus, or red phosphorus, or noisy arrows that made loud sounds.

Zhen (箭) were arrows not shot with bowstrings, usually blown through pipe-shaped poles called Di (笛).

Xiao (笑) used the character for "laugh," but was a hidden weapon; it referred to pouches put in the mouth.

They were used to widely spray or spit poison filled inside like a kingfisher.

She explained that it was good to aim at the eyebrows, because if the eyebrows get soaked, the poison would penetrate the inside of the eyelids even if the eyes were closed.

Then all sorts of shaped hidden weapons were laid out.

"This is my favorite dart, also known as a throwing star, with two separately rotating weights attached so its trajectory undulates like waves, and once it's embedded in the flesh, it digs in like this, this, and this way…"

Tang Lan-ah described the scene of the hidden weapon burrowing in with hand gestures.

Usually, when talking about something one likes, one's face shone brightly.

Tang Lan-ah, the Most Beautiful Woman in Sichuan who was usually as bright as the sun, was overflowing with an innocent and pure loveliness unlike her usual self.

Qing looked at that beautiful face and thought.

\textit{It's a bit off-putting when she's talking about poison and hidden weapons burrowing into flesh with such a bright expression…}\footnote{Qing herself cheerfully discussed how to dismember bandits in chapter 111}
