\chapter{Tang Clan's Paper Flower (1)}

Everyone had a memory of a taste that was etched in their mind and wouldn't go away.

However, whether that delicious memory remained because it was truly tasty, or if it was just a temporary excitement due to the body and emotional state, could only be known by eating it again later.

Like the snack bar from the days of receiving school lunches.

Qing had developed such a thing too, and it was the citron honey cold tea she drank last night.

She couldn't distinguish whether the citron honey tea with the secret ingredient was delicious, or if her body, having sweated a lot, was just crazy about the cool liquid.

So Qing thought about asking for a cup and visited the Tang Clan Clinic to find Tang Lan-ah.

\textit{By the way, were there always this many patients?}

The servants and maids were busy carrying medicinal herbs and decoctions, with lines of patients filling the Seven Great Gates.

Perhaps because of this, Tang Lan-ah looked very haggard.

Her skin, which was always clean with powder, was pale without makeup for some reason, and her hair was roughly tied up without being washed.

Her lips were dry without rouge, and there were dark circles under her eyes, making her look like she hadn't slept for days.

Last night she had disappeared clutching her stomach.

\textit{Did she perhaps get a stomach illness?}

\textit{They say doctors can't cure their own illnesses, after all.}

"You don't look well. Are you okay?"

"W-Wot?"

Tang Lan-ah jumped at this.

Somehow, her eyes were full of resentment, and they even started to moisten.

"You ask if I'm okay? Last night, I… Yesterday."

Tang Lan-ah's mouth opened and closed as if she couldn't bring herself to speak, and finally, a single tear rolled down her cheek.

"If it's that hard, why don't you just go and rest?"

"Hmph, do you think I'm as free as someone like you? There's chaos because of the Ouyangji Juice, I can't just not show up because I'm a little tired."

"Ouyangji Juice? Do you mean that carp juice?"

"That's right. Right now, there's a mild Combination Poison symptom spreading widely, but we don't know where the bee venom came from…"

Ouyangji Juice, true to its name, had no poisonous properties on its own and was completely harmless when ingested.

However, when combined with the poison of the Hongtousuanglifeng, it would cause high fever and rashes, making people sick for days. If blue ant venom was added to that, it would transform into a deadly poison that could make people struggle between life and death.

So, if the Five Poison Sect was actually bringing in Hongtousuanglifeng as suspected, they must have been sprinkling boric acid on flower beds and shaking trees throughout Chengdu.

Yet they hadn't found a trace of bees. And even though they hadn't, people showing mild symptoms of combined poisoning had started lining up at the Seven Great Gates over the past few days.

"How?"

"Those crazy bastards seem to have grown vegetables."

Since there was only one clinic in Chengdu, the Tang Clan Clinic, they had examined all those patients and concluded that when they investigated the vegetables commonly eaten, bee venom components were found.

The shocking conclusion was that they seemed to have cultivated the vegetables by mixing bee venom into the water when watering them.

"Then can't you just stop people from eating them?"

"We've already identified several. If they keep changing the items, we can't help but be late in responding. For now, we've told people not to use river water and we're putting counteragents in the wells, but…"

Since the water wasn't stagnant, it was like pouring water into a broken pot.

"Then can't you just get rid of the Ouyangji? Like a poison that selectively kills only Ouyangji?"

"Are you going to keep saying stupid things? Where would such a poison exist?"

"What if you mobilize all the fishermen?"

"We've already put out a bounty of one silver sycee per fish to try and reduce the numbers, but even after ten gold sycees have gone out, the water still remains the same. It seems like those bastards are buying them from Yunnan instead of catching them at Dujiangyan."

"Then what if you explain the situation and ask for cooperation?"

At this, Tang Lan-ah looked at Qing as if she was pathetic.

"If we do that, half the people in Chengdu will run away, half of those who remain will become bandits, and the rest will just end up shedding blood for no reason. Isn't that so?"

"Ah. Right."

Qing realized her mistake.

This was primitive, uncivilized, uncivilized, uncivilized China.

It was a world where one couldn't expect mature civic consciousness and shouldn't expect it.

Then suddenly, a thought occurred.

"Anyway, we just need to get rid of the Ouyangji, right?"

"What, are you going to slaughter them with that oh so great Dao Technique of yours?"

"No. Just say it's good for virility."

Tang Lan-ah frowned.

"What the? What does that even mean? How does that make any sense?"

"Why wouldn't it? Look at those vigorous and special salmon, I mean carp, that have come all the way up from Yunnan against the current. Surging up the river! Ascending all the way up! Something's rising! Who knows what it is, but it surely is rising! Ah, it really is good, but I can't really explain it."

Tang Lan-ah's face turned bright red.

"S-Such v-vulgar words. How can you say such embarrassing things out loud?"

"Anyway, there's no harm in trying, right? If it works, great, if not, then that's that."

"And if we do it that way, the people who eat it will be properly pickled in Ouyangji Juice."

"Didn't you say there was a counteragent or something? Tell them to boil it together with that and eat it."

"Hmm…?"

Tang Lan-ah seemed to think for a moment, then her eyes suddenly lit up.

"Wait? Then I'm going to say it was your idea, okay?"

"Then what else would you say? Were you planning to pretend it was your idea?"

\textit{Is it because her eyes resemble a cat's?}

\textit{Why does she look so evil just by her eyes lighting up?}

\textit{Or is her face just naturally a bit hateful?}

Qing thought this as she nodded her head.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A few days later, at Dujiangyan.

Countless fishermen cast their fishing rods with their ankles dipped in the riverbank.

Not just the riverbank, but fishermen on boats in the river were spaced at regular intervals, their eyes bloodshot as if they were prospectors out looking for gold.

"Oooh, it's coming, it's here!"

A fisherman's fishing rod bent like a bow.

After a struggle with the bending rod, a plump Ouyangji was pulled out, pierced through its forehead.

Amidst envious glances from around, several fishermen slowly inched closer.

Originally, there was a basic rule among anglers (fishermen) not to invade another person's territory.

If not, lines would get tangled, thus only increasing discord between them, and the fish would just eat the bait and leave.

For some strange reason, the fishermen who broke this rule were always old guys in casual attire, as if on a neighborhood stroll.

And this was true for Zhongyuan as well.

Or perhaps this trait originated from the continent and spread to various regions.

At any rate, the truth lies deep in the river and cannot be known.

Meanwhile, some were even throwing nets, but they were just releasing the miscellaneous fish they pulled up because the only species they were after was the Ascending Ouyangji.

Ascending Ouyangji!

It was named Ascending Ouyangji because it was said that if you boiled and ate it, even your thing would ascend with it.

‘Where else would that virility come from, having come all the way up from distant Yunnan against the current?' was what they said.

Moreover, it was also said that thanks to this, the Tang Clan Lord had seven sons in a row because his Yang Qi ascended.

The rumor had already spread widely, with dozens of people claiming to have seen effects, making it seem efficacious.

However, even fake medicine could have great effects due to people's belief, so it couldn't be said to be a complete lie.

There were some who said it had no effect.

But the prevailing theory was that they must have mistakenly bought fakes sold in the market.

And so, during the harvest season, an unexpected wild Ouyangji craze blew through.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In Tang Lan-ah's eyes, Ximen Qing was a dhole… no, not quite a dhole, more like a six-month-old kitten with a wild nature, always looking for an opportunity to embarrass her.

So she had conveyed Qing's suggested method to the household conference with great confidence.

'You see! Young Lady Ximen! Came up with a solution! While putting her name on the line! And her honor too! Even her Master's name! Saying she'd take full responsibility if it didn't work!'

'Ah, so, what it is is…'

'Ouyangji is good for… so, we should spread a rumor.'

'It's good for that, you know, that…'

'So, like what that is is…'

'You know, that… that thing…'

'Ugh, the cock!'

'…The phallus. The Yang Thing.'

She felt embarrassed alone afterward, though, not knowing what to do with herself.

Anyway, the household members said there was no way people would go out fishing over such a simple trick.

Especially in such a busy season. No way they actually do such a thing.

One Elder even expressed his discomfort, saying it was treating the people of Sichuan like complete idiots.

So it was two weeks ago that Tang Lan-ah, with a red face, inwardly rejoiced.

"Hoho, that's right. Since that's what men care about most, the Ximen child has hit the perfect weak spot. She indeed made such bold claims for a reason."

"I didn't know Young Lady Ximen possessed wisdom as well. I thought her words and actions were only frivolous."

"Isn't it as if everyone living in Chengdu has received grace from the Young Lady?"

"To solve a problem that twenty gold sycees couldn't solve by just spreading a single rumor!"

Thanks to this, her status rose practically vertically from a pretty beggar who just ate food to a wise girl whose true nature was hard to fathom.

"No! Why?! Why did that work?!"

Only Tang Lan-ah fumed alone.

However, once the water returned and the clinic became less busy, there was another side effect.

"So, perhaps tonight, together on a boat…"

"You punk, how dare you try to make a move in front of me? Huh? How dare you."

"No, wait, Elder Brother. How can you interfere like this?"

Because the Ouyangji couldn't even last two weeks before being nearly wiped out, the Tang Clan Clinic returned to normal.

This meant that once again, the burdensome flirtations of the five brothers plus the chagrined youngest and the first son walking on pins and needles had begun.

If they were bad guys, she would have slapped the shit out of them, telling them to lower their eyes.

But these were very brothers who had taken care of patients, even cutting into their sleep when chaos broke out due to the Combination Poison of carps and bees.

There was only one safe place from these brothers in the Tang Clan, and that was the women's clinic in the corner of the Tang Clan Clinic.

It was because, officially, there were no female physicians in Zhongyuan.

This was because physicians did not recognize women as physicians.

Instead, women who learned medicine were called 'Medicine Hags', which meant old women who just decoct medicine.

Or it was also used as an insult meaning someone who looked like a lowly beggar, hunched over and merely gathering herbs.

'Hey, you Medicine Hag of an old woman.' was how it was used.

However, if someone said such things in Sichuan, they wouldn't die peacefully of natural causes, because the women of the Tang Clan were basically female physicians who studied medicine.

As a result, they detested men entering the women's clinic.

Even the seven direct descendants of the Tang Clan were reluctant to enter due to this pestering pressure.

As such, Qing immediately took refuge in the women's clinic.

Because of this, Cui Liweng undeservedly received cold treatment, but since he was an old man who always had a gentle expression and lowered himself to show courtesy to everyone except young men, he was respected after a short while.

And so, while Qing was watching the examinations from behind Tang Lan-ah, simultaneously embarrassing and annoying both the physician and patients while taking refuge, it happened.

As the next patient came in and approached quietly, only Qing could see their Evil Karma. And that very person said…

"Nemesis of the Most Senior Brother! DIEEE!"
