\chapter{Tang Clan's Paper Flower (11)}

The sunset-colored Sword Qi enveloped the Moonlight Sword and shone.

At that moment, Zhao Guo's mind raced quickly.

\textit{Burning sunset-colored True Qi. A characteristic of the Divine Art of the Divine Maiden Sect, the Heart Cleanse Mirror of Zhu Xiang. So it is not a lie that she's Ximen Surin's disciple.}

The Imperial Palace martial artists were those nurtured by the Emperor, who gritted his teeth in his frustration to subdue Wulin.

They were familiar with all the major martial arts of Wulin and knew their weaknesses and countermeasures.

And the Yue Maiden Sword is not a problem.

The Yue Maiden Sword Technique was originally used by the State of Yue's soldiers and had been passed down, still occupying a place as an introductory martial art when entering the military.

Of course, Zhao Guo could perform it with his eyes closed.

\textit{I haven't heard of the Divine Maiden Divine Palm. Is it a martial art created by Ximen Surin? If she dared to name it Divine Palm, it must not be ordinary.}

\textit{But it didn't seem like a mere Peak Realm master's Hand Arts would be dangerous to an Unrestrained Realm Master using Force Armor.}

\textit{It shouldn't be too tricky. Except for that unknown old Buddhist over there.}

Both Cui Liweng and a Buddhist martial artist would take offense at this thought.

Anyway, that was the conclusion Zhao Guo came to.

In fact, a duel between a Peak Realm martial artist and an Unrestrained Realm Master was not much different from a fight between a child and an adult.

Although it was petty to accept a life-or-death duel just because a child (extremely) misbehaved, it wasn't that he lacked confidence in subduing her, even if it might be troublesome.

That's what he thought, but…

Suddenly, the Sword Qi rose one chi from Qing's blade.

This was a technique absolutely impossible with Sword Qi, not Sword Force.

If Sword Qi could be extended freely outside the sword, wouldn't everyone carry a small dagger in their pocket and draw it out to wield like the lightsabers in that famous work, instead of carrying heavy swords?

So it wasn't Sword Qi rising.

If one looked closely, it wasn't actually Sword Qi, but high-density Sword Threads clustered together to appear as one.

While the effects of the Yijin Cleansing Method were still unclear, at least one thing was certain: the blood vessels where True Qi flowed through the Eight Extraordinary Meridians had greatly expanded, allowing for what was essentially an ultra-high-output True Qi spray.

In terms familiar to modern people, it felt like double Qi consumption for one and a half times the power.

However, Qing's Qi Accumulation had already far surpassed her realm, and Sword Qi that hadn't formed into Force didn't consume much True Qi anyway.

"First move!"

Qing shouted as she drew a straight line.

The thick Sword Qi collided with the Force surrounding Zhao Guo's sword.

Though there was no sound as the swords didn't directly meet, a shockwave burst out from the center, blowing wind in all directions.

However, Qing's expression contorted while Zhao Guo's face relaxed slightly, so the result of the first clash was clear.

\textit{Ah shit, Sword Threads still don't work, huh.}

Zhao Guo's sword not only penetrated Qing's Sword Qi but also slightly chipped the blade of the Moonlight Sword.

Force Compression was merely a basic long-range technique that Unrestrained Realm Masters could use.

For those who weren't expertly handling Force Arts specializing in Force Compression, its power wasn't even as good as throwing hidden weapons imbued with Force.

So the true terror of Unrestrained Realm Masters lay not in Force Compression, but in the fact that they could emit Force compressed to a higher degree around their weapons, visible to the naked eye.

Purple Force rippled around Zhao Guo's sword, increasing its thickness.

It was a scene that would make the Daoist Monks of Mount Hua foam at the mouth.

It was the Imperial Grace's Violet Mist Arts, the Imperial Palace's modified version of the Violet Mist Divine Arts.

Qing was startled and withdrew her sword, but a large chip had already been taken out of the blade.

\textit{My Moonlight Sword!}

\textit{I barely even got to use it!}

Qing, who now had to obtain Moonlight Sword No. 9 after barely using this one, smiled awkwardly and spoke.

"Oh. Since you're such a Master, how about giving me ten moves as a handicap?"

"Nonsense!"

Zhao Guo's sword moved busily.

The Imperial Grace's Demon-Conquering Sword was a vicious killing sword forged with the terrible determination to subdue demons.

However, the compatibility was a bit bad, as the Demon-Conquering Sword was one of the martial arts with the strongest killing intent among Orthodox Faction techniques.

It was awkward to try to attack while avoiding the opponent's vital points with such a killing sword.

For Zhao Guo, whose family would be annihilated if Qing died, the enemy's vital points were as good as his own.

"Whoa! Eek! Ack! Ah, ah! Ah! Kyaak! Ack!"

Qing was busy dodging while continuously letting out breathless exclamations mixed with screams and admiration in a chaotic cacophony.

If she clashed directly, her sword wouldn't survive.

For now, it was a trick to distract and look for an opportunity by making noise.

However, no matter how much the attacks avoided vital points, the opponent was an Unrestrained Realm Master and an expert of the sword. Moreover, his swordsmanship was a peerless Divine Art.

If Qing had checked the Martial Arts Window, she would have seen the dazzling Purple Border of the Demon-Conquering Sword.

Qing twisted her waist to dodge the Force-imbued blade by a paper-thin margin.

However, the sharpness of Force extended beyond what was visible to the eye.

It immediately cut through her clothes at the waist along with her skin, causing a red stain to spread slightly.

"Ack! Wait! I really got cu- Kyaa!"

Small cuts gradually increased on her thighs, sides, and shoulders, causing her clothes to become patchy in just those areas.

Though she had clearly dodged, her skin split and stung, and while the pain made her worry about her condition and whether she had been badly cut, the aching wounds oddly didn't feel too bad…

"Ack!! Ack! Ack!? Hm? Huh? Why? What?"

Qing's exaggerated cries gradually subsided.

\textit{What's this?}

\textit{It clearly hurts? But it's unexpectedly okay?}

\textit{No, how should I put it.}

\textit{It feels hot and not that bad.}

\textit{The stinging, prickling sensation is strange, mysterious, like the pleasurable pain of scratching a mosquito bite…}

As a result, Qing's evasive movements became more concise.

With less unnecessary movement, her gaze became steadier, and as her vision stabilized, her movements became more efficient, allowing her to avoid sword strikes without incurring further wounds.

Zhao Guo immediately noticed the anomaly.

\textit{This wench, isn't she gradually becoming more adept at evasion!}

Zhao Guo, his anger rising, shouted.

"Damn you! What are you trying to do! Do you plan to keep dodging?"

"Then!? What else should I do!? Should I let you hit me!?"

Shouting thus, Qing's knees suddenly bent.

With her feet still on the ground, her upper body became parallel to the ground, supported by her arms.

Zhao Guo hesitated for a moment, having lost sight of Qing who suddenly seemed to sink into the ground and disappear.

This was a technique of a highly refined Movement Technique called Dragoon\footnote{Starcraft reference}, no, the Iron Plate Bridge.

From that position, Qing pushed off the ground with her arms, appearing to Zhao Guo as if she had suddenly sprung up from below his field of vision.

Qing made her surprise appearance and thrust her sword forward.

"Hmph! It is futile!"

However, the difference in realms was just too great.

Zhao Guo casually swung his sword, deflecting Qing's arm holding the sword and leaving her wide open.

At that moment, Qing's eyes flashed, and her left hand suddenly shot out.

Pak! Zhao Guo hurriedly raised his forearm to block.

Then he spread his left hand and curled his fingertips, taking the basic form of a Claw Technique called the Claw Hand and swinging.

Imperial Grace's Divine Wind Claw.

If a Daoist Monk from the Kongtong Sect had seen it, they would have screamed that he had stolen the Divine Wind Ghost Claw, their sect's hidden True Supreme Technique.

However, the White Hand Demonic Arts, even without its demonic nature, was one of the most mystical Hand Arts in the world.

By stabbing with fingertips, curling to scratch, slicing with the edge of the hand, then striking with the back of the hand, pushing with the palm center, and hitting with the raised joint bones of just the index and middle fingers, six moves were executed in one breath.

Since using the entire hand was called Hand Arts, it was truly the essence of Hand Arts in consecutive strikes.

As the Claw Arts he had learned as an auxiliary skill fell short of this, Zhao Guo's Force-wrapped hand was barely able to forcibly endure and deflect the blows it received.

At this moment, the right arm that had gone far out returned.

Sword Qi erupted explosively from Qing's sword again.

The moment Zhao Guo's gaze turned towards it, a chillingly red White Hand dug in and struck his side.

Using that rebound, Qing leaped back to widen the distance.

Although she had landed a few nice hits, Qing's expression was dark.

"Agh shit, Force Armor. It's so hard to have fun, huh."

Qing muttered while shaking her tingling left arm.

In contrast, Zhao Guo's expression relaxed a bit more.

"Ha. So you did have something up your sleeve. Fine, I'll acknowledge the finesse of your techniques. But don't you know that the difference in realms is as vast as a mountain? If you withdraw now, I shall show the generosity of a senio- Hmm?"

Zhao Guo, who was trying to persuade her to retreat with words, suddenly frowned.

A strange, chilling, tingling sensation suddenly surged from his side.

His left hand and forearm also felt subtly cold and stinging.

Zhao Guo quickly probed his meridians and detected the presence of a secretly penetrating dark energy.

A chillingly unorthodox dark energy was tearing through his blood vessels and spreading faintly, but strangely, it was simultaneously entwined with an orthodox warmth, reducing the pain and making it hard to notice immediately.

This showed that Qing's Divine Maiden Divine Palm, which mixed True Qi, had surpassed the viciousness of the original White Hand Demonic Arts.

"What, this, this is."

Only then did Zhao Guo notice Qing's chillingly white and long, world's most beautiful slender hands.

Wasn't it human nature to assume that if someone's face was that of a peerless beauty, their hands must naturally be beautiful too?

But now that he saw it, a martial art came to mind.

"This is the White Hand-"

"WAAAH!!! WAAAAAAAH!! HERE I COME AGAIN!"

Qing shouted and charged in again.

This was Qing's method of interrupting people's words.

At the same time, she firmly gripped the Moonlight Sword with both hands and pushed it out to the side of her shoulder, causing its radiance to burst out roughly, mixing brilliantly in red, white, and purple hues.

Anyone could see that this was clearly a final move using all her strength.

Starlight also flowed thickly from Zhao Guo's sword.

He intended to cut through the sword completely and break her spirit.

The huge sword of Qi that had extended beyond Qing's shoulder suddenly shot forward.

A massive streak of color drew a thick line in the air.

The Force-wrapped sword opposing it seemed rather small and diminutive in comparison, but everyone present instinctively knew it was the more dangerous, destructive starlight.

And just as the two energies were about to clash!

Qing's sword flew weakly into the sky with a Whoosh.

Of course, when you let go of an object you were swinging with all your might using both hands, it was bound to fly far away.

Zhao Guo had been trying to cut through the sword by meeting its trajectory.

With Qing's sword gone, Zhao Guo's sword only cut through the air, and his clenched hand went on an excursion far out to the side of his ribs.

"Opening!"

Qing's right hand went behind her back and firmly grasped the handle of a long object.

It was the end of a Ten Thousand Year Cold Iron short staff with a noisy miscellaneous function attached.

As Zhao Guo gritted his teeth and raised his Force Armor to the maximum, Qing used all her strength to swing Fushen-di upwards at an angle from below.

WHACK!!!

Fushen-di, imbued with a monstrous strength that even General Xiang Yu would have to acknowledge, struck the side of Zhao Guo's chest.

Zhao Guo's heels lifted off the ground as he lost his balance and staggered.

While Force Armor could block the impact transmitted to the body, it couldn't do anything about the pure physical force pushing him.

If he had known in advance, he would have withstood it with Thousand Catty Weight.

However, how could he have imagined that a slender girl, aside from her tall stature and ample chest, would exude such monstrous strength?

Qing alternately swung Fushen-di and her left hand with brute force.

Cui Liweng had said when criticizing Kicking Techniques:

A martial artist's strength comes from a firmly planted center, from the earth.

So Zhao Guo, having lost his posture and center of mass once, was pushed onto the defensive.

He could only desperately endure by wrapping himself in Force Armor, hunching his body, and continuously backing away.

Qing was also desperate.

Even in this situation, she wasn't getting the desired sensation of flesh tearing and bones breaking.

\textit{Seriously, what the fuck is Unrestrained Realm? Is it invincible!?}

\textit{I want Force too! I want to use Force!}

\textit{How am I supposed to live as a mere Peak Realm without Force? It's so unfair!}

\textit{But if I keep hitting, he'll die eventually, right?}

\textit{Who am I?}

\textit{The genius of the century who killed an Unrestrained Realm despite being only Late Stage Peak Realm.}

\textit{I have to brag to Master about this.}

Just as Qing was thinking this and about to raise Fushen-di again…

Suddenly, a chill ran through her entire body, causing all the fine hairs to stand on end and her skin to rise in goosebumps.

It was the killing intent of an Unrestrained Realm Master.

Qing's instincts reacted to the enormous murderous intent, the thought and Qi response of 'I will definitely kill you'.

"You, BITCH!!! DIE!!"

Qing hurriedly planted her feet on the ground and pushed her body in the opposite direction.

But she was already a step too late.

The trajectory of starlight traced a crescent moon as it swept across Qing.

Slash.

The sensation of skin tearing and a blade entering the body came clearly.

She also learned that when properly cut, sound was transmitted through the body, not the ears.

And then, more than the pain, what surged up was rage like a raging fire.

\textit{No, this son of a bitch! How dare he cut me!?}

\textit{When all he is is a piece of shit motherfucker with a shitton of Evil Karma!}

\textit{A fucker who only did bad things!}

\textit{He should have just given me Practice Points and died quietly!}

\textit{This shouldn't be happening.}

\textit{At least, I shouldn't be cut by such a son of a bitch.}

\textit{This is unfair.}

\textit{Bad guys should get cut by swords and good people should receive all the fortune.}

\textit{And I'm the most righteous person in the world.}

\textit{The most important and precious person in the world, you know.}

\textit{Yet this NPC, a piece of shit worse than an animal, dares to harm me without knowing his place?}

In Qing's pupils, a malevolent red star stretched awake and shone brightly.
