\chapter{Tang Clan's Paper Flower (7)}

Qing then focused on the Exchange Window again.

\textit{For now, let's just efficiently put this one to Six Stars and hold off on the rest.}

\textit{If I go crazy later, I'll raise it bit by bit and use it like a purification spell.}

After finishing the 2,000 Point Exchange, Qing frowned as she called up the next Exchange Window.

"Why 3,000 Points…"

\textit{Shouldn't it be 2,500 Points after 2,000 Points?}

\textit{Why is it showing 3,000 Points?}

She grumbled with a sense of injustice, but in fact, wasn't it common sense from numerous previous experiences that these kinds of exchanges gradually consumed more resources?

It meant that from now on, exchanges would be one for every increment of 1,000 Points instead of 500.

What was even scarier was that she didn't know if it would be 1,500 or 2,000 Points after this, and what made her even more afraid was that she didn't know how many she could exchange for 1,000 Points.

\textit{Damn, if I knew, I would have postponed the Yijin Cleansing Method.}

However, regret always came too late.

If the Yijin Cleansing Method had known, it would have given the teaching of ‘What can you do about what you have already learned? This Buddha has already settled in your dantian, so is it not my victory?'

What she thought were two free martial arts turned out to be just one.

Her future expected income had also dropped to less than half.

Qing sighed and put away the Exchange Window.

This was a judgment that she should subtly ask her Master later and decide.

Then she called up the Martial Arts Window and raised the Yijin Cleansing Method to six stars.

Qing stared at the Martial Arts Window for a long time.

Then, as she focused on one point, the bar filled up and the number changed, finally reaching Twelve Stars, the Grand Star.

White Hand Demonic Arts. Grand Star.

\textit{Wasn't it said that when it reaches Grand Star, I'll become indestructible below the elbow?}

\textit{And I can't grasp the Transcendent Realm at all yet.}

\textit{So I should have more means to counter Sword Force.}

\textit{Plus, there's Gramps to help with performance testing.}

\textit{Above all, blocking Sword Force with bare hands?}

\textit{Isn't that so cool?}

Qing roughly estimated her remaining Practice Points and raised one Purple Martial Art all the way to Twelve Stars.

Buddha's Palm, Grand Star.

Come to think of it, although it lacked a satisfying feeling, no martial art had been as helpful as Buddha's Palm.

Qing roughly unfolded the new Movements that had burrowed into her brain like parasites.

It was an amazing sight of wielding White Hand Demonic Arts with her right hand and Buddha's Palm with her left.

If someone had seen it, they would have rubbed their eyes and checked again, lamenting, 'Even with open eyes, I'm seeing things. What use is sight, whether you have it or not!'.

Moreover, freely using completely different martial arts separately with the left and right hands was a marvelous skill of itself.

It was such a difficult technique that only peerless Divine Arts or the results of developing the Upper Dantian made it possible.

But Qing hadn't trained martial arts by practicing with her body from the beginning.

She just pulled out certain movements embedded in her brain, so what did it matter if it was the right hand or left hand?

Qing was freeloading in many ways.

\textit{Or hmm. What if I learn some kicks?}

\textit{Hold a sword in one hand, tear with the other, shoot palm strikes, and when needed, I can kick too.}

Qing thought this was a good idea.

However, when she actually looked for Kicking Techniques in the Martial Arts Window, there were no Purple ones at all. In fact, there was only one Gold one called Formless Kick, and even Red Borders were few and far between.

\textit{What's this? Are Kicking Techniques underdeveloped?}

\textit{Was it ahead of its time or something?}

Because Qing couldn't contain her curiosity, she asked Cui Liweng, upon which he clicked his tongue and answered.

"The feet are the beginning of all martial arts. Whether you extend a spear, sword, or fist, the feet move first and support the body to exert force, so aren't almost all martial arts used together with the feet? So learning Kicking Techniques separately is not like Finger Stances of the Left Hand or Clasped Hand Techniques that can be used together. It's enough to learn just one as a trump card."

"Ah. Then what about the martial art called Formless Kick…?"

"Isn't Formless Kick a Supreme Technique of Shaolin? They are fundamentally people who take a Clasped Hand approach, so they made a few foot skills at least."

"Oooh. Shaolin."

"However, for a woman, it might be good to learn one. Women's skeletal structure is advantageous for Kicking Techniques, and if used as a Noble Kick, it can be quite tricky to deal with. If you ask your master, she will probably teach you one."

The Noble Kick wasn't a specific martial art, but rather referred to Kicking Techniques performed by women wearing skirts.

Its power was doubled because the shape of the legs could be hidden under the skirt.

In a way, it was close to a vile deception, but who would complain about a woman wearing a skirt?

There would be no problem as long as men didn't wear skirts to take advantage of the Noble Kick.

However, the act of fighting in a skirt itself was uncomfortable and interfered with footwork, creating a disadvantageous situation, so it wasn't particularly worth targeting for training.

This was why female martial artists often wore indecent skirts with slits on the sides.

Thus, all the mysteries were solved.

Kicking Techniques were trash!

If the Shaolin Monks heard this, it was a conclusion that they would nod at with crumpled faces.

While one couldn't say that Formless Kick or Demon-Subduing Cyclical Divine Kick weren't excellent supreme techniques, the truth was that it was better to learn other Divine Arts instead.

"Hmm, Gramps, then if I had to learn just one martial art, what do you think I should learn?"

"Well. In my opinion, I would like you to learn the Violet Mist Divine Arts."

"Violet Mist Divine Arts?"

"Do you not handle various True Qi with your special abilities?"

"Huh? You knew?"

"How could I not know that much?"

Cui Liweng snorted.

Although Cui Liweng had ultimately benefited greatly by dispersing his Demonic Arts and gaining a more precious Divine Art, he had ended up breaking apart all his previous achievements.

However, Qing had readily accepted and learned everything, handling True Qi of various different colors, so he thought there must be a way to use them without conflict.

But since he hadn't seen the purple energy of the Purple Lightning Demonic Arts, he thought she was being mindful of people's eyes.

"Since Violet Mist Divine Arts and Purple Lightning Demonic Qi look similar and cannot be distinguished by eye, if you learn it, couldn't you use it without worrying about the eyes of others?"

However, Cui Liweng was misunderstanding something.

Qing wasn't not using the Purple Lightning Demonic Qi, she just couldn't use it.

Purple Lightning Demonic Arts was originally a martial art that should appear in the form of lightning, rising up at will according to the owner's emotions.

However, in reality, it was busy running away from the Blissful Maiden Arts day and night, continuing a pitiful sprint without being able to do anything, along with other Demonic Arts.

As such, the Demonic Arts had set up a cute plot to revitalize themselves through Qing's automatic cultivation in order to counter the Blissful True Qi. However, they had ultimately despaired in the face of one Buddha and now collapsed because of two Buddhas.

Anyway, Qing, who wasn't particularly concerned about Purple Lightning Demonic Qi, wanted a different answer.

"What about besides Inner Qi Cultivation Techniques?"

"If it's swordsmanship, wouldn't the Wisdom Sword of Tai Chi be the best? Its subtleties are in tune with the principles of the world, so it should help with your growth and achievements too."

"Wow. Tai Chi!"

Violet Mist Divine Arts, Wisdom Sword of Tai Chi.

Qing scanned them and saw that both had dazzling Purple Borders, indicating they were Divine Arts.

Come to think of it, she had been too negligent with swordsmanship.

Even the Yue Maiden Sword Technique that had reached Grand Star wasn't actually a Sword Technique, but a blade technique!

The Divine Maiden Sword Sutra had an exhilarating taste to it, but it was Blue.

Ximen Surin had evaluated that it was much better to embody the rigidly formalized peerless Sword Art of the Yue Maiden Sword Technique rather than learning new Sword Techniques. Thus, she just focused on sparring (disguised as nuclear bombings).

In the end, it meant she didn't have a single proper Sword Technique.

Of course, in Qing's standards, proper martial arts were only those with purple borders, what the world called peerless divine arts.

Gold ones were barely usable.

\textit{Come to think of it, there seemed to be a Gold Sword Technique registered, right?}

\textit{Why wasn't I learning it?}

\textit{Was there some side effect?}

Qing seriously tried to recall, but couldn't remember anything, so she quickly made a decision.

One of the Ten Great Demonic Arts Under Heaven, One Hundred And Eight Asura Sword.

Six Stars achieved.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tang Lan-ah seemed to have realized that sleeping close to someone else was quite a difficult task.

This could be seen from the fact that she didn't ask to sleep together again afterward.

\textit{Well, of course it is.}

\textit{It's a privilege that only someone with a dull mind like me can do.}

\textit{Carelessly attempting it could be a big mistake that might mess up your sleep cycle.}

After spending several days training like this, the day of the decisive battle finally dawned.

From early morning, a group of arrogant people appeared, kicking open the gates of the Tang Center.

Of course, it wasn't a surprise attack but a bold walk down the main road, so the elites of the Sichuan Tang Clan, who had received advance notice, rushed out in droves to meet the enemy.

The fatty standing in the center, who looked exactly like a personification of Dong Zhuo, opened his mouth.

"Hah, you treasonous bastards. How dare you not move your heavy backsides when His Imperial Majesty ordered you all to come out voluntarily, forcing this esteemed Imperial Censor to come in person? Just how much of the people's sweat and blood have you sucked to fill your toilets and make your behinds so heavy?"

\textit{Ooh. That's a pretty hard blow from the very start.}

Qing recalled Tang Touzhong's words.

They shouldn't strike first when the other side was openly coming to provoke them.

At that, Tang Touzhong responded politely.

"Come out? We clearly heard that you would come to visit, so we should wait, did we not?"

"Tsk tsk. Isn't that the same thing?"

Then the Imperial Censor clicked his tongue again.

"Even if that's the case, the attitude of you traitors is incredibly disrespectful. I clearly said to wait with the appearance of criminals. So are you saying that this is the appearance of criminals?"

If they were criminals, they should have been kneeling with their hair down, wearing hemp clothes, with their forearms and knees touching the ground.

However, everyone was standing proudly on two feet, hence his words.

Despite hearing this, Tang Touzhong remained dignified.

"What do you mean? How can we call ourselves criminals over mere slander when we have committed no crime under these heavens? Is it not a crime against His Imperial Majesty for those without guilt to claim guilt and obscure the true culprits?"

"Hah. Your words are flowing like a mountain stream. Fine. Then let us find out from now on whether you really plotted treason or not. Look here, all of you, rush in and scrape out every single letter without missing a single thing."

"Ah. That would be a bit difficult."

Tang Touzhong interrupted the Imperial Censor's words.

"What? Then are you admitting that you plotted treason? That is proof that the evidence is in there!"

"That is not it. In truth, last night, a mischievous wild cat caused havoc in the warehouse, and unfortunately, it ran around with a pouch of deadly poison in its mouth, turning the entire Tang Center into a trap no different from an area of death."

It was an implausible excuse from the start.

If it was a poison warehouse, it should have been handled as one of the most dangerous places, so the idea that a cat got in there was ridiculous to begin with.

Moreover, was this cat carrying the deadly poison pouch in its mouth some kind of invincible, super cat with Invulnerability of Ten Thousand Poisons?

Even if they generously assumed that an invincible cat actually existed and raided the poison warehouse, how could it spread poison all over the vast Tang Center to turn it into a death trap without an infinite pouch?

At this, the Imperial Censor was utterly dumbfounded. So much so that his nose was blocked, his mind muddled by the nonsense, and his words cut off, leaving him only gaping his mouth.

Qing admired this.

\textit{Wow! Your Honor!}

\textit{It was all the cat's doing!}