\chapter{A Wicked Woman Eats Malatang (6)}

There's a saying that a woman's tears are beautiful.

That's bullshit.

In fact, there's no such saying.

When crying, the brow furrows downward while the cheekbones rise up, causing all the wrinkles around the eyes to appear in surprise as they fight each other.

Meanwhile, the mouth takes on a terrible shape, carving deep lines like the character for 'eight'.

The face turns bright red, tears flow in four streams from both sides of the eyes, and in severe cases, the catastrophe of snot bubbling up can occur.

This was previously demonstrated by Chen Cangming's wailing.

So clearly, there was almost no such thing like the crying from dramas that didn't yet exist in Zhongyuan - the kind of crying where tears gracefully roll down a beautiful face, making one think "How lovely she looks, even when crying."

But the reason there was 'almost' none was because it did exist in some cases.

It was when one had to swallow their sorrow and smile, showing restrained sadness, or when pretending to cry forcefully.

Tang Lan-ah was clearly sobbing uncontrollably with her mouth, but her tiny face remained beautiful.

Moreover, with moist eyes looking up pitifully and tears dripping down, even Qing thought 'Wow!'.

So Qing looked at Tang Lan-ah and thought:

\textit{Wow, how can she control her emotions so instantly like that?}

\textit{And in front of all these people?}

Meanwhile, Tang Lan-ah was getting goosebumps at her own wickedness.

Originally, women's schemes were largely divided into two categories.

One is the 'Who's the Biggest Bitch' category.

And the other is the 'Who's the Biggest Victim' category.

Although the term and usage of 'crocodile tears for the win' had not yet been established in Zhongyuan, truth inherently shines, even across ages.

This was the secret technique that created the current Speaking Poison Flower, the Most Beautiful Woman in Sichuan.

Tears of Flowers Filling the Sky!

When tears of flowers fill the entire sky, who in the world would not sympathize?

In an instant, she had captured everyone's attention and transformed into a pitiful and lovely beauty. In terms of pitifulness, she had far outmatched the veiled woman who couldn't proudly show her face due to her looks, or the grandfather who was a Master in the Unrestrained Realm.

\textit{I've won this fight, haven't I?}

Tang Lan-ah quickly saw her flustered opponent and raised her crying voice even louder.

"I'm so... sorry. Hic, sniff, waaah..."

"..."

"Hic, hiccup."

"..."

"I'm sorry, please, forgive me, hic."

"..."

\textit{What's going on? Why aren't they forgiving me?}

\textit{If they leave it like this, won't they be the ones losing out?}

\textit{Won't they just be cursed as a heartless grandparent and grandchild?}

\textit{Don't they care about their reputation? Are they throwing away their reputation?}

Tang Lan-ah had underestimated her opponent too much.

If they had cared about their reputation, they wouldn't have rolled on the ground three times, then wriggled around before neatly pocketing a gold ingot.

"Hic, hiccup, sniffle, sniff, sob, sorry."

However, now facing a formidable opponent, Tang Lan-ah realized the fatal weakness of Tears of Flowers Filling the Sky.

It consumed an enormous amount of mental and physical energy, and if she couldn't achieve a quick victory, she would be the one in trouble.

Human tears weren't infinite, after all, and her emptied tear ducts were screaming for her to stop.

Tang Lan-ah drew poison from the Poison Dan in her dantian and redirected it to her eyes, overworking her tear ducts.

These flowing tears were an extension of her Poison Arts.

At the same time, she kept thinking sad thoughts.

\textit{Right, like when Father scolded me just for breaking his precious vase.}

\textit{When practicing Hidden Weapon Techniques, he had only placed the most expensive ones on either side of the target to create a sense of urgency.}

\textit{It's not like I broke it on purpose, but he got so angry. He really went too far.}

\textit{It was the same when I roasted and ate the Thousand-Year Fleeceflower Roots.}

\textit{How could the world's most precious daughter not be allowed to roast and eat a mere elixir? How could he fly into such a rage over some guest's gift?}

\textit{Surely his daughter is more important than someone's 60th birthday present. He really went too far.}

This resentment became the driving force that extended the duration of Tears of Flowers Filling the Sky once again.

"I'm sorry, hic, please forgive me, waaah, hic, sniffle, hic, wahhh..."

These were the tears of none other than the Most Beautiful Woman in Sichuan.

The onlookers clutched their chests at her pitiful state, inwardly thinking that surely it was time to forgive her. This proved that beauty was indeed power and authority.

If just one person had taken the lead, everyone would have been on the verge of chanting in unison, 'Forgive her, forgive her.'.

That's when Qing finally opened her mouth.

"Ah. Come to think of it, doesn't this mean we can go eat malatang now? Gramps, let's go. They say it's the signature dish of the Greatest Chef Under Heaven, so we should try it."

"Even so, how great could malatang possibly be?"

"Haiya, don't say that before trying it. My good friend, let's go too. And don't think this means you're off the hook for treating us to dinner. A man shouldn't speak with two mouths, right?"

"That's right. I feel like even that much wouldn't be enough to pay for the show we've seen. It's quite satisfying."

And with that, the three of them slipped inside Azure Dragon.

Tang Lan-ah, left alone kneeling, was flustered.

Oh no. What should I do in this situation...?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Peng Chaolei was starting to feel like her time was being wasted.

In the time it took to do all this, she could have swung her dadao one more time, and it would all have been nourishment for her robust body.

She didn't really know what malatang was, and a true Wulin expert's dinner should be a whole roasted piglet or young calf, cut up and eaten.

Where had Tang Lan-ah gone after leaving earlier, and why were these three unfamiliar people giggling as they entered?

Peng Chaolei quickly scanned the three people.

Qing met that gaze directly.

\textit{I should probably greet her, right?}

\textit{I need to clear up the misunderstanding about the impersonation too.}

"Hello? Um, you're Daesan-er's older sister, right? I'm Ximen Qing, Daesan-er's friend. He hasn't told you about me, but... well, he never really talks about himself."

Peng Chaolei asked with a puzzled expression.

"Hm? Daesan-er? Does that brat let people call him that? He's not the type to allow that."

\textit{Ah. They're definitely siblings.}

Seeing Peng Chaolei's suspicious gaze, Qing hurriedly fumbled in her bosom and pulled out a guest plaque.

"I really am Daesan-er's friend. Look, this is what Daesan-er gave me as proof of friendship."

Peng Chaolei looked at the guest plaque Qing proudly held out.

She saw gold-leafed characters engraved in a majestic handwriting.

Nan'gong!

Peng Chaolei's eyes narrowed.

\textit{What's this? Is she showing off?}

\textit{Is she saying she's an honored guest of the Nan'gong family?}

"Nan'gong...?"

"Ah. I must have taken out the wrong one."

Qing held out the correct guest plaque this time.

On the gold-leafed plaque, deeply engraved characters filled with red pigment could be seen.

Peng.

The red and blue silk threads attached to it confirmed it was indeed a guest plaque directly from the heir, Peng Daesan.

Moreover, it was a top, top-tier plaque among all its ranks.

"Oh my goodness. It's real? You're really Daesan-er's friend? That brat has a girlfriend?"

"Since putting those two words together sounds a bit weird, could you call me his female friend instead?"

Qing answered with an expression of utter disgust.

A shudder of sincere dislike, completely identical to a certain someone's.

Peng Chaolei burst into hearty laughter.

Judging by the sound alone, it was closer to a mountain bandit's laugh than that of a female expert from one of the Five Noble Clans.

"I see, a friend? Purely just a friend? Yes, that's right. That brat should experience this once too, for a change."

Peng Chaolei's eyes became incredibly warm.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was quite some time later when Tang Lan-ah came in.

If she went back right away, it wouldn't seem like she had truly reflected even after crying, but she couldn't just keep kneeling awkwardly outside either.

People kept gathering to see the Most Beautiful Woman in Sichuan, but those who were supposed to accept her apology had just gone in without a care. It was truly an unprecedented situation.

So Tang Lan-ah, gritting her teeth, slowly looked around before getting up and returning, only to find...

A scene of warmth and laughter, with Peng Chaolei's expression, which had been as dull as peeling garlic before, now sparkling with unprecedented vitality.

\textit{What's this? Why is the atmosphere so good?}

\textit{Sister-In-Law, you weren't like this with me.}

Tang Lan-ah inwardly shed tears of blood.

Renting out an entire restaurant like Azure Dragon was a bit of an overreach, even for the Tang Clan.

It was a place she had forcibly arranged, half-threatening that it would block her marriage prospects, but now some random bitch was gobbling up the place she had protected by kneeling and shedding tears.

Tang Lan-ah's eyes burned with fire.

\textit{This humiliation cannot be endured.}

\textit{I must show the true terror of the Sichuan Tang Clan.}

Vile Venom? Or Intestine Melter? Or perhaps Eyebrow Pimple Poison?

Tang Lan-ah recalled the poisons she possessed.

Vile Venom caused a burning sensation in the nose, triggering a waterfall-like nosebleed. Intestine Melter, true to its name, caused a storm in the toilet. Eyebrow Pimple Poison was such a terrifying poison that it made a volcano-like pimple erupt between the eyebrows. Truly worthy of bringing forth the tears of a woman.

Tang Lan-ah was the Speaking Poison Flower, a incomparably wicked woman who always carried such extremely dangerous deadly poisons.

"Ah. Lan-ah. This is Qing'er, I mean, Young Lady Ximen Qing. Have you two met already?"

\textit{Er?!}

'Er' was originally a term of endearment used by parents for young children, usually attached to the front or back of the last character of the name.

When attached to the front, it was more formal and could be used in official settings, while attaching it to the back emphasized affection particularly.

Using Peng Daesan as an example, it would be 'Er San' or 'San'er'.

It was also used to address someone as close as a younger sibling.

However, an older male should absolutely never use it with the 'er' at the end when addressing a younger male.

This must be emphasized with 'absolutely' a whopping three times.

Remember.

'Listen, Er San'. (Good)

'Listen, San'er'. (Public Enemy No. 1 in Wulin)

"That, um, did you two... know each other...?"

"Huh? No, we just met today."

"Urgh."

"What's wrong? Are you sick? Does your stomach hurt? You're groaning. Anyway, Qing'er, so as I was saying. When I was killing those bandit bastards..."

"Ah, I think I know. If you cut off the limbs first, the way they squirm..."

"Right, and then if you lay the head like this..."

"I know. When you smash it, that crushing sensation..."

"Ooh, you know! Then, making them vomit their intestines through their mouth..."

"Not there, if you hit the spleen area a bit harder..."

Although she couldn't understand, some kind of ominous conversation was taking place.

Was this really a topic for women to discuss?

Nevertheless, what was clear was that the atmosphere was very warm and friendly.

\textit{I don't mean it literally, but I feel sick in the stomach.}

At the same time, cold sweat was pouring down.

\textit{This won't do!}

\textit{I need a topic that can break through this situation!}

That's when it happened.

-AAAAAARGH!!! AAAGH!!! UWAAAAAGH!!!

Suddenly, a scream full of anguish rang out.

It was a scream that chilled the listener to the bone.

A horrific sound echoing from the kitchen.

Thanks to this, the conversation was interrupted and all attention turned towards the kitchen.

Tang Lan-ah shot a gaze as bright as stars towards Yan Ruoang, who was serving as both her guard and uncle.

\textit{As expected, Uncle, I believed in you!}

\textit{You do come through once in a while when it counts!}

Yan Ruoang responded with Sound Transmission.

-It wasn't me. So stop looking at me like that.