\chapter{A Wicked Woman Eats Malatang (1)}

Chengdu, the central city of Sichuan Province.

Though famous as the capital of Shu, it had been a prosperous ancient capital at the center of Sichuan even before that.

Among the vast basin surrounded by mountains that is Sichuan, it was close to the most fertile land and heavenly mountains. It could be said without exaggeration that it was in a location bestowed by heaven.

Among these areas, the western district of Chengdu, Chongzhou County, was a street that developed adjacent to the Min River.

The Min River, with its gentle currents, was the perfect place for floating lantern-lit boats.

Naturally, a port town that developed along such a river would be densely packed with all sorts of taverns, teahouses, red and blue brothels, and gambling dens for pleasure-seeking tourists.

Let's say a tourist came to Chengdu.

The first day would be spent shedding tears and snot from the numbing Sichuan cuisine, then realizing with a refreshed body afterwards that this is the true joy of mala, the pleasure of spiciness.

Though they might have to suffer a bit at night.

On the second day, one must visit Mount Qingcheng.

The famous Qingcheng Sect was located on the front mountain, after all.

The back mountain, with its gently rolling, not too rugged terrain and diverse vegetation, had been praised as the most serene landscape in the world.

If lucky, one might even see a Giant Panda!

Despite its name meaning 'giant bear cat', it was actually a type of bear, not a cat.

If Qing had seen this lovable creature, she would have immediately exclaimed in admiration,

'Wow, a panda! You know about pandas, huh!'

Then, after enjoying the sights like Dujiangyan, Wuhou Shrine, and Wenshu Monastery on the third and fourth days, one might be at a loss for what to do next.

And that was when you should go to Chongzhou County.

You can float boats on the Min River, drink, gamble, and have a wild and fiery time.

And when you start to get bored of that, that would be when a suspicious man would approach.

'Ah, Big Brother, I see you've been enjoying yourself. Perhaps you'd like to see something really exciting?'

If you follow the man with half curiosity and half suspicion, you'll soon find yourself descending stairs underground, passing through a long corridor, and reaching a vast underground plaza with a huge stage in the center.

And this would be the Underground Life and Death Arena, Chengdu's famous attraction that everyone who knows about it knows about.

Cockfighting was called "douji".

And human fighting for gambling was called "touji", making this place, where mortal combat took place every day, the pinnacle of gambling for life-and-death duels.

Today, too, the Underground Life and Death Arena was hot.

The blue stone floor was drenched in blood and human remains, giving an idea of the heat.

The host, with his smooth-talking skills, mesmerized the audience.

"Finally, today our challenger has issued a challenge to one of the Four Heavenly Kings! For ten straight days, he has slain one Peak Realm fighter each day for eleven days! This challenger from Hainan! Please welcome him with loud cheers!"

The iron door under the cave opened.

A man walked out, his footsteps echoing.

"The ghostly left-handed swordsman, the Sword Ghost from Hainan, the Tael Yaksha, Yik Taikong!"

The audience responded with passionate cheers.

Then the host continued shouting with a volume that made one worry his throat might burst.

"Which great expert among the Four Heavenly Kings of the Underground Life and Death Arena has accepted his challenge? They're appearing now!"

The opposite iron door opened, and a figure wrapped from head to toe appeared.

Only the eye holes were open, but even those were covered with a veil, making them invisible.

For a woman, she was quite tall, dragging an enormous dadao that even a strong man would struggle to wield.

"Responding to the challenge is the third-ranked among the Four Heavenly Kings of the Underground Life and Death Arena, the great expert Female Xiang Ji! A mysterious woman whose face no one in this world knows, the second coming of the warrior Xiang Yu6 in the human world! Female! Xiang! Ji!"

"----!!!"

An enormous reaction erupted, incomparable to before.

It was almost like a collective frenzy had broken out.

Female Xiang Ji responded to the cheers by raising her hands high and waving them around, in stark contrast to her heavy entrance.

In fact, if any of Qing's acquaintances were there, they might have asked why she needed to cover her entire body.

Finally, the two stood face to face on the life-and-death arena, messy with blood and remains.

"Female Xiang Ji? What a laughable wench."

It was a light jab typically thrown before a life-and-death battle.

However, when it came to the art of yapping, Qing had already passed the Natural Realm and reached Ascension, thus finding only the Immortals her match.

Female Xiang Ji's glib speech was already famous, having been seen by many spectators.

But Female Xiang Ji was also known for picking and choosing who to deign such divine words towards. If they were worth or not of such a stellar yapfest.

"Eh, he ain't all that, huh... Let's end this quickly."

Qing wiggled her fingers.

At this, Yik Taikong's eyebrows twitched.

"Ha. Very well. They call you Female Xiang Ji, so let's see how mighty your strength is to warrant such an arrogant na-"

Yik Taikong's words trailed off.

Whoosh! Whoooosh!

The sound of something heavy cutting through the air was terrifying.

It was a massive weapon, five chi long with a blade width of one chi, likely weighing well over twenty catties.

When wielding this massive weapon in one hand and swinging it as lightly as a tree branch, the sound alone made one's knees weak.

It was a sight that would make the faint-hearted kneel immediately.

Regardless of martial arts proficiency, it was simply not a humanly possible act to begin with.

"Y-Your strength certainly lives up to the name Female Xiang Ji. However, martial arts are meant to overcome such differences, and a true martial artist like myself will use my skills to…"

Yik Taikong's words trailed off again.

Dao Qi rising from the massive blade.

But was that really just Dao Qi?

Didn't it almost seem like the Yellow River itself was flowing from the dao?

Qing's Inner Qi in its pure quantity was at the Unrestrained Realm, and in its very end stages at that.

Lacking enlightenment, she couldn't compress it to form Force, so she could only use it with brute output.

The result was a blade of Inner Qi rising a whole chi thick.

Yik Taikong shouted boldly in response.

"I concede! Today, this Yik has greatly realized that I am nothing but a frog in a well! As they say, a person should withdraw when they realize their shortcomings, so would you please allow this humble one to withdraw?!"

At this, the audience erupted into a riot of curses and mockery.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Zhi Fasheng, the vice leader of the Underground Life and Death Arena, wore a very displeased expression.

Of course, because today's match, which should have been the greatest attraction, had ended so anticlimactically.

"You didn't kill him today, huh?"

However, Qing answered.

"Hello? Excuse me, Mr. Zhi. If someone heard that, they might think I'm a Demonic Adept who kills people every day. I'm such a kind person, though. I'm a righteous female expert from the Orthodox Faction, you know?"

"...? You always claim that, but…"

Zhi Fasheng just blinked his eyes.

The audience of the Underground Life and Death Arena tended to be more enthusiastic and cling to fighters who were more cruel and vicious.

And Female Xiang Ji was the most popular fighter in the Underground Life and Death Arena.

In Female Xiang Ji's matches, the concept of gambling itself changed.

After all, instead of who won, people bet on how many pieces the opponent would be cut into today.

Female Xiang Ji was indeed in the Late Stage Peak Realm, so she was put in Peak Realm matches.

But because she was on a winning streak with skills that were originally in a different league, betting on wins and losses wasn't very interesting.

So they made money in a different way by betting on how many pieces the opponent would be cut into or how many rounds they would last.

However, occasionally, like today, she would quietly send her opponent away without touching them, so they had suffered from complaints from customers today as well.

"At any rate, this kind of thing is troublesome. We're trying to make a living here too, you know? So, from next time, we'll put you in Transcendent Realm matches."

"What? I'm in the Peak Realm, so why should I fight in Transcendent Realm matches? I'll just quit instead."

At this, Zhi Fasheng gently rubbed his palms together, as if pleading her.

"Don't be like that. We'll match you with someone who just entered the Transcendent Realm, so give it a try. With your innate strength plus that massive weapon, you should be able to win easily against that level."

"Hmm. Is that so?"

Qing gently stroked the chin area of her mask.

Her realm still hadn't risen, and perhaps she needed to face someone Transcendent Realm or higher rather than weak opponents.

Originally, the biggest problem when facing Transcendent Realm opponents was Sword Force, as it was impossible to compete with just Sword Qi.

But after blocking Gramps' Force a few times, she found that lacking Enlightenment could be made up for with brute output of Inner Qi.

Of course, the exchange rate was terrible.

If using Force took 10 units of Inner Qi, it took 50 or 60 units of Inner Qi to just crudely push out Sword Qi.

That was why the wall between Peak and Transcendent Realms had been considered so important since ancient times.

Not only was the exchange rate terrible, but the amount of True Qi was also much greater in the Transcendent Realm.

Unless one stupidly consumed Elixirs or had special circumstances like Qing, the level of Inner Qi at the Peak Realm was more or less the same for everyone.

Moreover, Qing's strength had now reached a state far beyond human limits.

No matter how advanced a martial artist's Inner Arts cultivation was, they couldn't ignore such an overwhelming difference in weight.

"Alright. I'll fight someone who just entered the Transcendent Realm in the next match, then."

"Good thinking. Here, take today's prize money."

Zhi Fasheng tossed over a pouch that looked quite heavy, even from just a glance.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Qing arrived in Sichuan, she had a plan.

First, she would stop by Chengdu to confirm that Ximen Xi was safe, then leave Cui Liweng behind for a while and visit the Emei Sect.

However, despite being told that a message would be left at the fifth largest brothel, there was no news even after searching every brothel in town.

When Cui Liweng asked why, she explained, and he clicked his tongue, saying:

'According to what you said, didn't you leave the cult first and set out? And then you rushed from the Heavenly Demon Tomb to Sichuan, so no matter how fast they are, they could not possibly be in Chengdu already.'

That's right.

Qing had arrived first.

However, that didn't mean she could just head to the Emei Sect because of this.

Currently, Cui Liweng was in too weak a state.

He was in the process of dispersing sixty years of Inner Arts and replacing it with a new Mind Art and Cultivation Technique.

So inevitably, and absolutely not because the Sichuan cuisine was particularly to her taste or because lazing around was too enjoyable, but really, inevitably, she had no choice but to stay in Chengdu. Even if just for Cui Liweng's sake.

But the cost of living in Chengdu was too high.

Originally, prices in famous tourist destinations were high, especially for outsiders.

It was even more so because overcharging outsiders was a very common practice in Zhongyuan.

It was natural for merchants, and even those being overcharged considered it perfectly normal.

Even if Qing got angry about being overcharged, Cui Liweng would just give a blank response asking what the problem was.

With no money and no way to earn it, she was wondering how to continue this idle life.

That was when she found out about the Underground Life and Death Arena.

It had already been a month and a half since then.

When Qing returned, Cui Liweng clicked his tongue.

"Tsk. Did you go to that vulgar place to sell your sword again?"

From Cui Liweng's perspective, it was understandably distasteful for her to be swinging a sword in such a suspicious fighting arena.

Qing frowned sharply.

\textit{Who do you think I'm going through this trouble every night for?}

Of course, since most of the fighters were evil people, she gained Righteous Karma Points and Practice Points for fighting them.

The joy of killing evil people and the cheers that responded to it made for the highest job satisfaction.

But still, no matter how fun and beneficial, work was still work.

"Didn't they say there's no high or low in professions?"

"...? What nonsense is that? How could there be no distinction between noble and base professions?"

"Ah. Right. That existed here. I got confused."

This was primitive, uncivilized ancient China.

It was a world where the nobility and baseness of professions were very clearly organized in tables.

"Anyway, Gramps. Hurry, hurry. Didn't I tell you to be ready in advance? I said we'd go right away when I got back."

"We can go like this. But, is eating really that good?"

"What? Do you hear yourself? They say it's the Ultimate Malatang. Ultimate, you hear? How can you resist the Ultimate?"

That's right.

It was the day Qing had made a reservation for.

The dish you must eat when you come to Chengdu.

The dish you must eat before you die.

The dish that people say you should stop by Chengdu for even if you have to cross Zhongyuan for just one bowl.

The Ultimate Malatang made by Bai Changzi, the Greatest Chef Under Heaven, was waiting!

\begin{quote}
	The chapter title is a reference of "The Devil Wears Prada" film.
\end{quote}