\chapter{A Wicked Woman Eats Malatang (9)}

Tang Lan-ah's expectations were shattered from the very start.

When the thick fat under the duck's tail is trimmed and roasted, it creates a chewy and crispy mass of rich fat with a different texture from large intestines.

This delicacy, which only yields a few pieces even from a large duck, was traditionally served in a golden bowl towards the seat of honor.

However, in the Tang Clan, there existed a separate, undisputed number one whose position no one questioned.

At least, that had been the case until now.

Just as Tang Lan-ah reached out with her chopsticks, the table suddenly rotated, and the second son swiftly picked up the golden bowl and placed it in front of Qing.

"Young Lady, would you like to try this? Originally, the most delicious part of a roasted duck is this fat under the tail."

"Really? Wow, what's this? Holy moly."

Qing's eyes widened.

\textit{What's this? Why is it so delicious?}

\textit{Have these petty Zhongyuan people been keeping such things to themselves?}

The first wife's eyebrow twitched as she watched.

\textit{Even mothers have mouths, you brat.}

\textit{They say raising sons is futile, and how right they are.}

Meanwhile, the third son was demonstrating his specialty.

Wielding twin chopsticks, he skillfully and quickly stripped the meat from the duck's neck bones, which was his area of expertise.

The deliciousness of poultry neck meat needs no explanation.

Tang Lan-ah, as always, expected her Third Elder Brother's caring gesture to arrive in front of her, but…

That plate naturally headed towards Qing.

"The tail is good, but we can't forget the neck. Would you like to try this as well?"

"Oh? I could just tear it off myself, you know? But thanks anyway. Oh. It's delicious. So good."

Qing's mouth relaxed into a smile.

Qing was a person whose emotions were clearly visible on her face.

The face of a happy beauty glowed with its own light.

The second wife simply resigned herself.

The plate that originally would have gone to her daughter was now heading towards the guest.

She thought this might actually be better.

\textit{Sister, it's not just raising sons that's futile.}

\textit{Don't think daughters are any different.}

\textit{They're all the same, those brats.}

The two wives exchanged glances.

No wonder the wives got along like sisters.

"Young Lady Ximen, this is called Jian Nan Chun, Sichuan's finest liquor. If you enjoy white spirits…"

"Wow, Jian Nan Chun!"

"Young Lady Ximen, by the way…"

"Young Lady Ximen…"

"Young Lady…"

A competition broke out among the brothers over the woman.

However, such a scene was absolutely not considered ugly in Zhongyuan.

This was because romance in Zhongyuan originally meant a state where men fawned over women, watching their every move and being completely wrapped around their finger.

In matters of love, women held ten tenths of the initiative over men.

Why? Because men could have multiple wives.

After marriage, this relationship completely reversed, and wives and concubines had to fawn over and support their husband to be loved more.

So before marriage, women were the absolute top dogs.

After marriage, it flipped, and men became somewhere between an awkward top and middle position.

It might seem unfair, but where in the world is truly fair?

In this Zhongyuan view of romance, quickly snatching the most delicious parts and offering them, or stripping meat from bones, was just the basics.

It wasn't even considered particularly sweet, just basic care.

They were just ordinary Zhongyuan men.

However, it was too blatant for Qing to handle, making her feel a hundred, no, a thousand, ten thousand times more burdened.

\textit{What's going on? Why is everyone staring at me while I'm eating?}

\textit{I have hands too, so why is everyone peeling, scooping, and cooling things for me?}

\textit{They look like they'd even feed me if I asked}. (They would)

\textit{So this is why Gramps insisted I wear a veil.}

\textit{I should have listened to my elders; there's nothing to lose by doing so.}

Qing regretted it belatedly, but it was too late now.

There was no use in covering up after revealing her face.

Of course, did this mean Qing ate less? Of course not.

Perhaps because the continent was so vast, the ducks were as big as baby pigs, and the meat, steamed with a spicy Sichuan method, was tender and greasy.

And so Qing inhaled the duck meat from the magical plate that automatically refilled itself, and gulped down the famous liquor from the magical cup.

People were such fickle creatures; even though she was eating without barely chewing, when a beauty did it, it somehow looked blessed.

Only Tang Lan-ah was left staring with wide eyes.

\textit{Is that a person or a pig?}

\textit{Why doesn't she just pick up the bowl and drink directly? She's stuffing her cheeks like a toad.}

\textit{And all my bastards of Brothers are dead to me.}

\textit{I'm going to tell on them to the adults.}

As the Speaking Poison Flower was grinding her teeth…

A Tang Clan warrior appeared, opening the door to the banquet hall.

He approached Tang Touzhong respectfully and whispered in his ear, then turned towards the table, clasped his hands, and said:

"A black flag has been raised at Grand Prince Dexian's prefecture."

"What? Who, who has passed away?"

Ziyou hurriedly asked.

"Well, it's said that Grand Prince Dexian has… passed away."

'Passed away' meaning he kicked the bucket.

The Tang Clan warrior answered, feigning sorrow.

It was a line that had to be delivered solemnly no matter what.

After all, if one were to sound excited, it would be treason.

"…?"

Meanwhile, there was Ziyou, who had suddenly heard news of his own death.

Ziyou's mouth gaped open in disbelief.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At that time, in the Demonic Cult's temporary improvised dungeon.

To cut to the chase, Xue Ganom and Ximen Xi had failed to escape.

It was already a done deal.

Blaming someone for it would only hurt the feelings within the group.

So instead of scolding Ximen Xi, Xue Ganom, true to his reputation as the neighborhood's top intellect, coolly pondered ways to escape again.

Ximen Xi's beauty, honed by the Blissful Maiden Arts, had improved over time, and they were in the middle of planning a honey trap based on that.

Fortunately, Ximen Xi had no aversion to using her looks as a weapon.

After all, that was the way of the Bliss Palace.

However, their plan to seduce the jailer and escape ended before Ximen Xi could even try her aegyo1 once.

Not that Xue Ganom had high expectations after seeing Ximen Xi's aegyo anyway.

"Um, that. Why don't you come out now?"

"What's this about?"

"A high-ranking person has ordered us to escort you politely. The food in prison is all we could offer, but we have not treated you poorly otherwise, have we?"

"…?"

It was quite fortunate for the jailer as well.

They had been so busy with overwork day and night that they had no time to play with prisoners, so they had just thrown them some dry rations.

They could have gotten into big trouble if they had bullied them unnecessarily.

Xue Ganom and Ximen Xi came out of the cell.

Then Shrine Maidens from the Divine Palace rushed over, washing them, scrubbing them clean, nourishing their bodies with elixirs, and even dressing them in fine clothes.

Xue Ganom lamented.

"I don't know whether to be happy or sad."

"Huh? Why?"

"The treatment is so polite, it's like receiving honored guests. If that's the case for us, it's only because of Young Lady Ximen's connections, so perhaps the Heavenly Demon has awakened and become connected to Young Lady Ximen."

"Ah, then does that mean my sworn sister is the mistress of the Divine Cult? Hmm, isn't that a good thing?"

"That depends on the individual. No matter how good a position is, it's not good if the person doesn't want it."

As they were talking like this, the door to the room opened and Zhi Shengzu appeared.

Xue Ganom immediately recognized Zhi Shengzu.

"I heard the Demonic Brain was a young boy, but…"

"It's a pleasure to meet you, Great Expert Xue. And Great Expert Ximen. This is our first time meeting like this. I am Zhi Shengzu. Though inadequate, I am the one in charge of the Secret Pavilion."

"Great Expert? What are you playing at right now? What's your angle?"

"What? Am I a Great Expert too?"

"There is no particular angle. It is just that you two are now in positions that deserve the Divine Cult's hospitality."

"What the… I'm being treated well? Oooh."

"…What has happened to Young Lady Ximen?"

"There is no need to worry. She is currently advancing into Zhongyuan."

"As far as I know, if she had gone to Zhongyuan, the Demonic Cult wouldn't be this peaceful."

"What? My sworn sister has already gone to Zhongyuan?"

"They say the ways of the world are unknowable, do they not?"

"Enough with the ambiguity. Get to the point."

"…? Can you not hear me? Isn't this kinda strange?"

The two intellectuals completely ignored Ximen Xi's words.

"She has inherited all the Divine Arts and descended as the Heavenly Demon Supreme. Before leaving, she ordered to open the doors of the Divine Cult and live more like humans now. The foolish long-cherished wish of liberating Zhongyuan has finally come to an end."

"…?"

Xue Ganom's expression became dumbfounded.

"Could you… say that again? That friend did what?"

"I did not expect things to turn out this way either. But Young Lady Ximen is now the Heavenly Demon Supreme of the Divine Cult."

"What? My sworn sister is the Heavenly Demon Supreme?"

"No, wait. I do not understand. What in the…"

"What what? Then what am I? The Heavenly Demon's Sister?"

"Could you please be quiet for a moment? It's distracting."

Ximen Xi closed her mouth dejectedly.

Xue Ganom thought of Qing.

She was the friend who said she would give the Demonic Cult bastards a taste of their own medicine, destroy the Heavenly Demon Spirit, and run away.

So, how did such a person suddenly become the Heavenly Demon?

However, if asked whether it suited her or not.

It was a perfectly fitting character, indeed.

After all, she seemed truly born to be the Heavenly Demon.

"Of course, she currently has no interest in the Divine Cult, but would the people of Zhongyuan think the same?"

"That's true."

"So we would like you two to assist the esteemed Heavenly Demon Supreme."

"You mean you want us to persuade Young Lady Ximen to return to the Demonic Cult?"

At this, Zhi Shengzu smiled faintly.

There was no need to hide his expressions anymore since he didn't have to cater to the Supreme's whims.

"Is there really a need for that? From what I have seen, the Heavenly Demon Supreme is someone who will return to the Divine Cult sooner or later anyway."

"…I can't deny that."

Xue Ganom agreed gloomily.

How long could a Heavenly Slaughtering Star who returned covered in blood every night endure staying in Zhongyuan?

"Great Expert xue, you cannot hide forever either, can you? The Heavenly Demon Supreme seems to be a person overflowing with affection, after all."

"What if I refuse?"

At this, Zhi Shengzu shrugged.

"Nothing changes. You may leave if you want, but if you are going to Zhongyuan anyway, just promise to serve the Heavenly Demon Supreme. If you do that, we shall provide you with the cult's elixirs. After all, having a higher martial prowess would be helpful in serving her."

Xue Ganom quickly came to a conclusion.

There was no reason for the Demonic Cult bastards to play tricks regarding their own Heavenly Demon.

In that case, there was no reason to refuse free elixirs either.

\textit{This is what having a good friend means, huh.}

He thought about how this was payback for all the times she splashed water on his face.