\chapter{A Wicked Woman Eats Malatang (3)}

The Five Flowers of Zhongyuan.

It quite literally meant that there were Five Flowers in Zhongyuan.

In other words, it meant no further explanation was needed.

Then suddenly, a thought occurred.

"Ah. This isn't actually something like the Five Great Beauties of Sichuan, is it?"

"What are you talking about?"

"Well, didn't you say earlier that the Culinary Competition for the Greatest Chef Under Heaven was actually the Culinary Competition for the Greatest Sichuan Chef?"

"That's certainly true for cooking, but not so much for Sichuan women. It is indeed the Five Great Beauties of Zhongyuan."

"Oooh."

If that was the case, Qing, as obviously a man among men, couldn't miss out.

After all, it was at least true that her eyes were pleased whenever she went around with Peng Guy.

"But if it's Speaking Flower, why is it Speaking Poison Flower? Is it because she uses poison?"

"No. It's because her personality is nasty."

"Ah."

\textit{Well, if she was the type to casually push aside other people's reservations, her personality must be more than just a little nasty.}

\textit{If she wanted to eat something delicious, she should have just come with two or three people and pushed out other customers besides herself to eat.}

\textit{They said she was from the richest family in Sichuan, so are they having a restaurant tour as a company dinner?}

\textit{And with enough people to rent out the entire place?}

\textit{What the hell? Now that I think about it, it's infuriating.}

Qing shouted in front of the canceled customers.

"How can there be such an outrageous thing in this world! The country has its laws, Wulin has its rules, so surely businesses must have clear business ethics!"

"The young lady is right!"

"Indeed, isn't business also part of Daoism?"

The canceled customers responded enthusiastically.

Qing shouted again.

"Are dishes more important than people! Restaurants make a living by serving customers, so we customers are the foundation of the restaurant and the most important among the ranks! Those fuckers who don't understand this and arrogantly cancel reservations as they please should just go bankrupt!"

"That's right! They should go bankrupt!"

"There's a limit to treating customers like dogs!"

"Everyone! This is not just about whether we can enjoy a single meal or not! If they continue to make money and thrive with such bullshit behavior, eventually all restaurants will treat customers like dogs! We must make such dog-like restaurants go bankrupt to show that justice is still alive in Zhongyuan!"

"Oh, oh! Right! That's correct!"

Qing passionately orated, asserting customers' rights with a fiery heart.

Previously, the canceled customers had gathered to vent their anger, comforting each other and wasting time in the process.

But now, enlightened by Qing's eloquence, they embraced the great ideology of customer-centrism and were reborn as fighters struggling for their rights at this moment.

And so a young fighter asked:

-But Madam. That arrogant shop is so famous that its reservations are already booked for a month and a half. Will our condemnation really affect their prosperity?

To which the madam replied:

-That is why we must treat those who crawl on their knees to beg for food from a shop that treats us like pigs and dogs with the excuse of being delicious as idiots.

They are no different from petty pigs and dogs who sell their dignity for mere food, and they harm the public justice of the world, so their hearts are also extremely wicked.

Therefore, if we all despise and curse those who say they have eaten Azure Dragon's food and shame them, won't they then know shame and stop going?

At this, the fighters finally slapped their knees and exclaimed in admiration, inwardly taking note and deeply engraving it in their hearts.

Qing's utterly wicked words were a new shock to the simple people of Zhongyuan.

It was an atrocity that might even earn her a place as the Progenitor of Mindless Power Tripping in the future.

If that happened, her honorary title following Confucius, Mencius, Zhuangzi, and Han Feizi might be something like Consumius or Consumzi. As a proud consumer, of course.

Anyway, as Qing was watching the canceled customers burn with their new mission with satisfaction...

"I didn't know my friend had a talent for sophistry and incitement."

"Hey now. What do you mean sophistry and incitement?"

Qing continued.

"Actually, you're right. Anyway, if they go bankrupt because of this, or even if their sales just plummet, I'll feel better. So isn't that good enough?"

"Now that I see, you are quite a malicious woman too, Friend. As Confucius said..."

"Hey now, Friend. Your way of speaking is becoming more and more like that of a noble person. Can you go back to how you were before?"

"Ah. I didn't realize. You're right. I'll keep that in mind."

Meanwhile, as the canceled customers were uniting and making a pact, they were just about to resolve to pour great jeers at the mysterious VIP customer who caused today's disaster as their first step.

That was when a huge carriage appeared in the distance.

On its luxurious black walls, large gold-leafed characters were boldly emblazoned.

Tang.

The momentum of the canceled customers who were about to pour jeers suddenly faltered, and they started to surreptitiously look around, distancing themselves one or two at a time and pretending not to be involved.

Thanks to this, the passionate discussion about customers' rights also abruptly ceased and disappeared.

"What's with these people? They were so fired up earlier. Why are they suddenly..."

"Who in Sichuan would dare to curse the Tang Clan?"

Qing's voice turned fierce.

"Well, well. Look at this shit. It's like an emperor has arrived. Anyone who sees this might think a king is making a royal procession."

"...That's right."

Ziyou agreed with a somewhat gloomy expression.

The carriage looked big even from afar, but it got even bigger as it came closer.

It was a carriage pulled by eight white horses, so naturally its majesty was extraordinary.

"That carriage looks really nice."

"Of course it does. It must be the top-of-the-line limited edition carriage from the One Thousand Trading Associations. They won't even take orders unless you have considerable power. That's the Eight-Headed Power Carriage, of which there are only three in Zhongyuan. Its exterior is made of ebony dyed by a master craftsman, fitted together without wedges, and also..."

Suddenly, Ziyou's words burst forth like a waterfall.

Ah, this guy was a carriage enthusiast.

Anyway, the gist was that this carriage was amazing, so Qing listened with one ear and let it out the other.

It seemed that whether in Zhongyuan or modern times, the behavior of people who couldn't control themselves when their favorite topic came up was the same.

In the meantime, Cui Liweng whispered quietly.

"Ahem. Child. Do you perhaps want that?"

"Huh? Gramps. We don't have money, you know?"

"We may not have money, but there are ways to acquire a carriage if we want to..."

"Nahhh. Forget it. Who wants to go around pulling eight horses? And how would we maintain it? It's enough to just rent one when needed."

"Well, that is true, but..."

Cui Liweng looked disappointed.

The One Thousand Trading Associations was one of the front businesses of the Heavenly Demon Divine Cult.

The ride quality of the prisoner transport carriage that Qing had ridden in was the culmination of that technology.

Qing had absolutely no interest in carriages.

Instead, she was interested in something else.

"So, you're saying one of the five prettiest women in Wulin is riding in that?"

"On the surface, that is certainly true."

Qing raised her expectations at those words.

After all, wasn't he saying that despite his obvious aversion to the Sichuan Tang Clan, he still acknowledged her beauty?

Finally, the carriage rolled up and stopped, and one of the coachmen leaped down with an impressive movement technique.

\textit{What the? Are they using Peak Realm Masters as coachmen?}

Qing snorted.

\textit{No, wait what? Why would a Master around the Peak Realm be working as a coachman? Do they not have any pride?}

\textit{Or do they pay that much monthly salary?}

\textit{Do they give one gold sycee per hour or something?}

As Qing was thinking this...

The coachman opened the door with a respectful attitude.

And finally, the Speaking Poison Flower, one of the Five Flowers of Zhongyuan and the Greatest Beauty of Sichuan, revealed herself.

The Great Beauty of Sichuan's foot first touched the ground.

The long skirt with slits on the sides was a popular outfit among Wulin women.

It was also unavoidable because skirts without slits were inconvenient for movement.

As she extended one foot first, the Great Beauty of Sichuan's robust leg was revealed through the slit.

\textit{Huh? Wot? Robust?}

It was a very robust leg indeed.

The thigh was thicker than Qing's waist, and the muscles asserted their presence by type, with clear texture and distinct boundaries.

A giant woman, as giant as the huge carriage, revealed herself.

She was about eight chi tall, but her presence was even more imposing than her height.

Even her forearms, not revealed by the sleeves, seemed to be of considerable thickness judging by their lines.

She was a beauty with a cheerful expression on a head atop broad shoulders.

She was certainly beautiful, but...

\textit{Wait, where have I seen her before?}

\textit{Why does she feel familiar?}

\textit{If I had seen such a giant woman before, there's no way I could have forgotten...}

At any rate, she was pretty enough to pass by with a passing thought of 'She's pretty', but not to the extent of turning around to look or stealing glances.

Instead, anyone would rub their eyes and turn to look just because of that powerful physique.

\textit{Ah.}

Qing realized her misunderstanding.

"So the Five Flowers of Zhongyuan are ranked by strength?"

"Hm? What do you mean?"

"Right, right. After all, martial artists should fight to claim their positions."

Qing looked at the Great Beauty of Sichuan's giant fist.

It was a fist that looked like it could take down a bear with one hit.

Since it was the Five Flowers of Zhongyuan, it must be a position that female martial artists fight to claim.

Then Ziyou spoke as if he found her pitiful.

"Isn't it obvious that she is Female Xiang Ji, Peng Chaolei? I heard rumors that Female Xiang Ji had appeared in the Underground Life and Death Arena recently, but I didn't know it was true."

"Uh... Female Xiang Ji was a real person?"

Qing, who had unintentionally become an impostor by using someone else's alias, looked around nervously.

For people of Wulin, impersonation was a serious crime tantamount to declaring someone your mortal enemy.

"It's my first time seeing her in person too, but indeed, she's a woman worthy of that alias."

And then he muttered with a worried tone.

-But for a daughter of the Peng Clan to come out in a Tang Clan carriage, if there are marriage talks, it would be extremely troublesome...

Qing only caught parts of what he said.

"Huh? Peng Clan? It's that Peng Clan?"

"Indeed. That very Hebei..."

"Your speech."

"Right. Yes, it's that Peng Clan of Hebei. She's the eldest daughter of the Peng Clan."

Female Xiang Ji, Peng Chaolei.

The name Chaolei used the characters for ‘crow-tit' and 'beautiful', given because the baby girl born after eight months was particularly small and petite, like a crow-tit.

However, no one could have imagined that she would grow so enormously tall afterward.

"Ah! No wonder. She looks exactly like Daesan."

She was the female version of Peng Daesan, the Most Handsome Man Under Heaven.

Perhaps that's why, while she was beautiful, she was the type of beauty that would be described as handsome among women.

Qing sighed in relief.

She had unintentionally become an impostor.

But since it was a friend's big sister, wasn't that fortunate?

She thought that if she confessed honestly, apologized, and explained the situation well, they might let it slide.

That's when it happened.

There was a woman who belatedly revealed herself, circling around the huge carriage.

She had gotten off on the opposite side.

And then she affectionately clung to Peng Chaolei's arm and spoke in a coquettish voice.

"Sister, you shouldn't look down on it just because it's malatang. I'm sure you'll come back with your family members again."

"I'm sure you're not talking about the whole family. You mean just one certain individual, right?"

"Hehehe... But, Sister, you really will be surprised when you taste it."

Qing was surprised too.

\textit{Woah! Holy shit! She's really pretty! Nah, that's crazy work! Is that even human!? How the fuck is that even human?}

\textit{Is this the caliber of the Five Flowers of Zhongyuan?}

\textit{Okay, then. Yes. I do hereby acknowledge the label, Five Flowers of Zhongyuan.}