\chapter{A Wicked Woman Eats Malatang (8)}

There was Grand Prince Dexian's prefecture in Sichuan.

This signified none other than a Grand Prince, the Emperor's own younger brother.

Although the Grand Prince has never officially shown his face, someone of the Tang Clan Lord's status, being the head of Sichuan's most powerful local clan, would have paid respects during major holidays.

And that very Grand Prince Dexian opened the door to the Clan Lord's hall and appeared.

\textit{What on earth had this crazy daughter been up to?}

One had to note that while a daughter was a daughter, a Grand Prince was a Grand Prince; someone far too important to ignore.

Just as Tang Clan Lord Tang Touzhong was about to bow deeply, Ziyou smiled and put a finger to his lips.

At this, the Tang Clan Lord froze in a strange posture as if diving into water.

"Dad? What's wrong?"

Then the problematic daughter rudely asked in informal speech in front of the guests.

It was truly a lifelong regret that he hadn't properly disciplined his lovely youngest daughter.

In the end, it was all his fault.

"Ahem, ahem. It's nothing. Didn't someone say this posture is good for the body?"

Tang Touzhong awkwardly crossed his legs and sat down.

It was a very uncomfortable position.

In fact, the relationship between the royal prefecture and the Tang Clan was not good.

For generations, Sichuan had been the Tang Clan's territory.

This was true even before the royal prefecture suddenly appeared and became the owner of most of the land in Chengdu.

So it seemed like a complex behind-the-scenes struggle over interests would begin, but the royal prefecture withdrew first, and since then, they had been gradually siphoning off interests.

Even so, his mind was racing furiously.

\textit{What possible reason could the Grand Prince have for visiting in secret?}

\textit{He had been living as if he didn't exist for the past ten years.}

\textit{Had they discovered the hidden saltpeter mine that had recently been found?}

\textit{And why with this ill-mannered daughter of all people?}

Suddenly, a bolt of lightning struck Tang Touzhong's head.

\textit{Ah. I see. So even the Grand Prince is a man.}

A Grand Prince would be a super-premium catch for a husband.

Not only was he of imperial blood, but he was fundamentally a person of upright character who could empathize with others and disliked conflict, truly worthy of being called a virtuous man.

Tang Touzhong's attitude became more relaxed.

He thought that perhaps he might benefit from his troublesome daughter after all.

The Tang Clan Lord pretended to be calm as he greeted each guest in turn.

"So, our esteemed guests. Oh. You are the Godmother's named disciple? How does the Sword Queen fair? I see, I see."

The Godmother's named disciple, Ximen Qing.

There was no reason someone at the level of the Tang Clan Lord's martial prowess couldn't see through the veil, so Tang Touzhong was quickly dispirited.

Well, of course. What did he even expect?

How could it make sense for his daughter, who had nothing going for her except her face, to become a queen?

Still, even the Grand Prince is a man after all, he thought.

"Ah, and this elder. Ah. Yes. I understand."

Just an old man taking care of Ximen Qing.

"It is you, Chaolei. How could I forget? Right. We met at Old Man Moyong's 70th birthday banquet. Is that Peng brat doing well? What's that? His realm has risen? Good heavens, does that kid just eat and swing his sword all day?"

Peng Chaolei.

In fact, beyond the Five Noble Clans, even among the Ten Great Clans, no, since the Jin Prefecture Yun Clan had disappeared, among the Nine Great Clans, there was no one who wouldn't recognize Peng Chaolei.

Not only because of her size, but once you heard the name "pretty crow-tit" for someone with such a build, it would be etched into your mind.

Wasn't it the case that even the Peng Clan Lord said he didn't know she would grow so much every time? He joked that if he had known, he would have named her Taisan (Great Mountain/Mount Tai) or Taifeng (Great Phoenix).

And finally, it was the Grand Prince's turn.

"And that noble young master over there...?"

"Dad, forget about him. He's just a weakling who tagged along."

"A weakling who tagged along. Also known as Ziyou."

"Ahem. Well, welcome."

Tang Touzhong nodded with an expression that seemed as if he had reached a state of Nirvana..

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tang Touzhong had two wives and eight children.

Seven sons in a row from the two wives, and at the end, a ray of light shone with the birth of a precious youngest daughter.

Seven older brothers. The two mothers, tired of the boys' heedless detachment, all the elders of the family, and even direct and collateral cousins would go crazy just looking at her, saying how pretty she was.

Moreover, she was objectively a beautiful girl with looks belonging to the Five Flowers of Wulin.

As such, was there any need to explain what kind of upbringing she had?

She was the very definition of Tang Clan's top dog, the family's greatest little villain.

It was only thanks to the Tang Clan's strict family traditions that she remained only a little villain.

Still, when adults scolded her, she would obediently kneel and cry while reflecting, so the child wasn't completely hopeless.

And that very little villain gathered all seven of her older brothers before dinner.

"Do you know how much humiliation I suffered from that veiled wench? I can't stand this! I won't stand for it!"

Tang Lan-ah breathed heavily.

The eldest son, Tang Jintie, looked troubled.

"Ah'er, no matter what, that woman is of an allocation equivalent to a great elder of Daoism. And it's only because we're a noble clan; otherwise, she'd be on par with the Grand Elder."

"What?! Dage\footnote{Great Brother}, are you serious? Your Lan-ah suffered such humiliation! In front of all those people, she made me kneel and apologize!"

"But how can we use poison on such an important guest..."

"Lan-ah cried and begged in front of everyone. Are you really my brother? How can you be so cold!?"

"Dage, doesn't Ah'er have a point? No matter if she's a Daoist elder or whatever, is there any justification for making a direct descendant of the Tang Clan kneel in the middle of the marketplace?"

"It's not like we're using any serious poison. She'll just have a stomachache. The seventh and I will pretend to have stomachaches and go back and forth at dawn. If there's a problem with the food and even the direct family members are affected, who would question it?"

"Ugh, Elder Brother. Me too?"

"As expected of Elder Brother Hyun! Elder Brother Jin is the only one I can rely on! Hmph, whose side are you on, Dage?"

"No, Ah'er. I just..."

"If that's how it is, Dage can just pretend not to hear. Third Brother, Fourth Brother, and the youngest will do the poisoning. With a Four Combination Poison, even a Divine Doctor couldn't detect it."

"Ugh, Elder Brother, do I have to do the poisoning too...?"

"While we're at it, let's rip off that veil too! I want to see how ugly her face is!"

"The seventh can pretend to trip and grab it."

"No, wait what? Elder Brother? Why do I have to do that too...?"

"Interfere with her eating too! Make noise next to her and spit while talking! Put half-chewed food on top of her dishes while laughing!"

"Isn't the seventh an expert at that? If the seventh sits next to that young lady, it'll solve the problem."

"That's a bit... I have my own dignity..."

"Alright. Then let's do it like that. But remember, everyone. Dage is the Young Lord, so he didn't hear anything."

"Brothers? What about my opinion...? Really...? Can you not hear me?"

"Heheng! My brothers are the best! Except for the eldest."

The Tang Clan's vile plot was deepening. However…

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The reason Qing wore a veil was primarily because Gramps was so overprotective.

Secondly, it wasn't particularly uncomfortable.

Among the Demonic Cult's sources of income, trade goods from the strange-skinned Semu\footnote{Categories of people who came from Central and West Asia, established by the Yuan dynasty} people beyond the mountains occupied a significant position.

Cui Liweng had visited the Sichuan branch of the Demonic Cult's Covert Operations Division and forcibly taken the most precious veil.

Originally, it was an item that was supposed to be presented to that Princess of Kaifeng. The merchant who heard the news foamed at the mouth, but, per usual, Qing knew nothing about that anyway.

It was indeed a precious item, not visible from the outside but providing clear vision from the inside.

Even when eating, she could just fold it once and adjust it at the tip of her nose, so she didn't feel much discomfort wearing it all the time except when sleeping.

And there was a third reason.

At first, the veil was fluttery and a bit annoying, but once she got used to it, it couldn't be more comfortable.

Didn't the Korean people before her journey into Wulin also cover the lower half of their faces with masks for peace of mind?

Physical discomfort could be overcome with familiarity, but mental comfort would settle in and become indispensable before one realized it.

However, if the reasons disappeared, there was no need to wear it.

The third reason:

Qing, who knew her own allocation, had entered a noble clan's house, so there was no need to be mindful of others.

There was no need to pursue mental peace.

The second reason:

The fact that it wasn't uncomfortable didn't mean it was comfortable.

And the first reason:

Even Cui Liweng's blood boiled a bit when he saw the Speaking Poison Flower.

In Cui Liweng's eyes, no matter how much they called her the Speaking Poison Flower or the Most Beautiful Woman in Sichuan, she couldn't even reach Qing's toes.

After all, even lowly cats, if pretty, were carried around and shown off to the neighborhood, weren't they?

(Though a cat, a territorial as they were, might be troubled)

And so, when Qing took off her veil, Ziyou just blinked his eyes.

"...?"

"What? Saw something you shouldn't have?"

"Friend?"

"What, is it awkward to see my bare face?"

Ziyou suddenly remembered a conversation where he had thoughtlessly asked if she didn't feel jealous when seeing a woman prettier than herself.

At that time, he had misunderstood her answer of why she would feel jealous.

Of course there was no reason to be jealous when the Speaking Poison Flower wasn't a woman prettier than herself.

"Did you really need to hide such beauty?"

"Ugh. Beauty my ass."

Qing got goosebumps and hit Ziyou's arm repeatedly.

"Ow, ow, stop, stop. It hurts. Wait, it truly hurts."

Ziyou rubbed his arm vigorously and shrank back.

He could instinctively tell.

It was the kind of hit that would leave a dark bruise by the next morning.

"Why don't you manage your speech? You're sounding more and more like you have a stick stuck up your ass."

"Ahem. It's become a habit, so I can't help it."

"Forget it, let's go eat duck. Ugh, I'm seriously starving to death. What time is it anyway?"

And so, Ximen Qing descended upon the Tang Clan's banquet hall.

Peng Chaolei, who had been carefully observing Qing's physique, immediately recognized her identity.

"Oh, Qing'er, you took off your veil? What's this, why were you hiding such a pretty face? That bastard. What did he say again? He doesn't look at faces? Doesn't look at faces, my foot. Well, why am I even surprised."

The first to move was the Tang Clan's fourth son.

The youngest, the seventh son, was flustered by the fourth's smooth intrusion.

"Uh, Elder Brother? My seat..."

"Haha. How dare you covet the seat next to your sister-in-law?"

"Wait, no, why are you suddenly..."

"That's enough, move, ugh."

Suddenly, another hand struck the back of his head.

"You should move aside too. Even cold water has its hierarchy. So how can you try to get married before your older brother?"

In the end, the second son took the youngest's seat and grinned while squirming with a dignified expression.

At this, Tang Lan-ah smiled with a venomous glint.

\textit{So Second Elder Brother is going to take action himself!}

\textit{Yes, I was a bit flustered because she's a tiny bit prettier than expected, but just you wait and see...}

But of course, in what world would things go as planned? Especially when Qing was involved?