\chapter{A Wicked Woman Eats Malatang (2)}

The term "prehistoric era" commonly used didn't just refer to ancient times.

It meant, quite literally, the era before (先) history (史).

In other words, it referred to the time before humans invented writing.

It signified the unknown dawn of humanity, a time without records.

However, surprisingly, there was a single record left from before the prehistoric era.

The estimated date of this record was over 10,000 years ago.

The academic consensus was that it was a record left by an advanced pre-human civilization.

This was the Hwandan Gogi, which recorded the history of the Hwanguk, the first utopia and empire built by pre-humans.

The truth of this Hwandan Gogi was even written in the Soo Bahk Do.

Of course, there were many people who misunderstood and failed to comprehend the reality of this majestic Hwanguk.

They were a race that had transcended the Three Thousand Worlds spoken of in Buddhism and surpassed the Nine Heavens of Daoism to reach the Heaven of Heavens.

If intelligence were to be expressed in numbers, ordinary people with an IQ below 1500 naturally couldn't understand it.

Only geniuses with an IQ of 1501 or higher could understand that Hwanguk was omnipotent and the ancestor of all current humans on the six continents.

The only intellect that could dare to oppose these geniuses would be another faction of geniuses who have realized the truth that the world is flat and set out to enlighten others.

As an aside, since extremes eventually meet, it might be impossible to distinguish between geniuses and imbeciles or retards.

According to the Hwandan Gogi, malatang was a traditional food of the Korean people and had been loved throughout its long history since it first appeared under the Divine Birch Tree.

This malatang spread to Zhongyuan and formed a primitive form of food called maocai.

(No, that's just bullshit)

Maocai is a traditional Sichuan dish.

They would carry around a hot pot and a basket full of various toppings separately, and when a customer ordered, they would combine them in a bowl.

It was also the most beloved food for customers who sought rich ingredients with many varieties, even if the individual portions were small.

And from maocai, malatang developed again, which honestly spoke to the principle of worldly circulation where malatang becomes maocai and maocai becomes malatang again.

And right there was the most excellent Ultimate Malatang in the current world.

Culinary King Azure Dragon.

The Greatest Chef Under Heaven Is Within.

There were two signboards hanging on the restaurant.

Along with an unusual name for a restaurant, there was even an additional signboard boldly attached below it.

"But 'Greatest Chef Under Heaven'? Gramps, do you know who decides these things? Is he just someone with great self-confidence? Or do chefs gather and determine rankings or something?"

"I do not know either. I have not heard of such a custom in Zhongyuan."

Cui Liweng was equally curious.

That's when it happened.

Someone naturally answered that question.

"That's the title given to the last winner of the Culinary Competition for the Greatest Chef Under Heaven."

"Oh. The Culinary Competition for the Greatest Chef Under Heaven."

Qing exclaimed in admiration, then tilted her head.

"Strange. My heart races just hearing the name, but why haven't I heard of it before?"

"Well, it's a cooking competition to select Sichuan's best chef, so how would an outsider know about it?"

"Ah. But why is it called 'for the Greatest Chef Under Heaven'? Shouldn't it be the Culinary Competition for the Greatest Sichuan Chef?"

"Well, since Sichuan cuisine is the best under the heavens, the best chef in Sichuan naturally becomes the Greatest Chef Under Heaven."

"We'd have to hear opinions from other provinces to know that. But who's our smart friend here?"

Qing didn't have a habit of describing men, and rather disliked it, so the details weren't important.

He was just the epitome of a sickly young master - pale-faced, weak and frail, yet with an air of nobility.

"Me? I am um... Zhang Liu, Zhang Yu would be good. My name is Ziyou. And the young lady?"

Zhang Liu looked at the long willow branch behind Qing as he spoke.

The very definition of a ‘long willow branch' was zhang liu.

Basically, he wasn't even trying to hide that it was an alias.

"So, is it Zhang You or Ziyou? Pick one."

"Let's go with Ziyou. I'm not close with the Zhang family."

"Alright. Ziyou. I'm Qing. Ximen Qing."

Then Ziyou replied with a grin.

"Good. Young Lady Ximen, is it? But why are you speaking informally?"

"Because you did it first? What, does it bother you?"

Qing asked while placing her hand on her sword hilt.

The implication was that if it bothered him, they shouldn't use words but swords.

Seeing this, Ziyou's smile grew even wider as he continued.

"To be honest, yes. But. Your words have a point, so I will not nitpick."

"Right. Ziyou. I have a habit of not making friends with suspicious people, you know? Thanks for the explanation, but shouldn't we each go our own way now?"

"Don't be so cold. It seems you're also going to eat Azure Dragon's Ultimate Malatang. Since it's come to this, why don't we share a table?"

"Me? Why?"

"I've ordered five liters of Wuliangye liquor, but it seems a bit much to handle alone. Perhaps you'd like to help?"

Wuliangye was a famous Sichuan liquor, even appearing in the Romance of the Three Kingdoms.

Meng Huo's younger brother, Meng You, surrendered to Zhuge Liang with a strategy similar to the mythical Trojan Horse, but Liang, knowing this in advance, served him Wuliangye.

The liquor was so delicious that Meng You forgot all about his strategy and just kept drinking Wuliangye until he passed out, thus failing spectacularly.

You see, Qing loved alcohol.

Having researched Sichuan's famous liquors, even Qing, who hadn't properly read the Romance of the Three Kingdoms even once, let alone three times, knew about this.

"Could it be from Yibin\footnote{a city in the southeast Sichuan}? It's from Yibin, right?"

Qing's eyes shone through her veil.

She had to wear the veil because old man Cui Liweng would nag endlessly otherwise.

"Of course. One cannot pair inferior alcohol with the dishes of the Greatest Chef Under Heaven."

Wuliangye of Yibin referred to the most precious among these liquors.

There was even a saying among drinkers that Yibin was worth risking one's life to drink.

Qing had tried it before, but it was a rare item that couldn't be accessed even with gold sycees.

Qing quickly nodded.

"Come to think of it, true friendship isn't shaken by a little suspicion. Friend."

"Friend... Good. Very good."

Ziyou smiled brightly.

Seeing this, Qing understood.

\textit{This guy? He has no friends.}

\textit{Then I can safely extort a hefty friendship fee from him.}

"But who is this elderly gentleman with you?"

"Ah. Gramps? Gramps is, well. He's the old man who takes care of me."

When it came to explaining Cui Liweng, that was all she could really say.

After all, she couldn't introduce him as a former Great Guardian and Great Demonic Adept from the Demonic Cult.

"I am called Cui."

"I'm pleased to meet you too, Old Man Cui. May I call you Old Man?"

"...Do as you wish."

Cui Liweng, who had been observing Ziyou, answered thus.

\textit{Clothes made of the finest silk, a pale face.}

\textit{Add to that the occasional casual condescension that seemed so natural, and anyone could see he was a young master from an extremely powerful family.}

\textit{That's three points right there.}

\textit{With palms free of calluses and a solar plexus like that of ordinary people, he clearly hadn't learned martial arts.}

\textit{So three more points.}

\textit{Minus five points for being frivolous enough to casually speak to a woman.}

\textit{Two points for being unpretentious and not caring about titles.}

\textit{Three points for likely not being an outgoing personality since he had no friends.}

\textit{A total of six points meant he was worth keeping an eye on for now.}

Cui Liweng's minimum required score started from 100 points.

As they were chattering like this and about to enter Azure Dragon's...

There was a group of people glaring at them with tilted postures opposite the entrance.

Since they didn't look like they had good intentions at first glance, Qing couldn't contain her curiosity.

"By the way, who are those people over there?"

"Ah. You mean the canceled ones?"

"Canceled ones?"

"People whose reservations were canceled."

Sometimes when circumstances arose where customers couldn't be received, the day's reservations inevitably had to be canceled.

The problem was the aftermath.

Reservations were backed up for a month and a half, so customers either stayed after making a reservation to eat the Ultimate Malatang, or they made a reservation through a proxy and visited at the appointed time.

Naturally, they were upset when it was suddenly canceled, and doubly so when they were just given back their deposit and left hanging.

"They just return the deposit and that's it?"

"What else can they do? Should they give them a new reservation a month and a half later, or push back the next day's customers to fill the spots? That's not possible either."

"That's true."

Qing nodded.

After all, when it came to restaurants, good food was king.

Customers were essentially paying money to get a mere taste, so the more successful a place was, the more they tended to close twice a week and take all public holidays off. They weren't that desperate, after all.

"So what are they doing over there?"

"Probably trying to protest or something."

"Those people really have nothing better to do."

Qing let out a hissing sound.

\textit{Sure, you'd feel bad if your reservation was canceled, but if they're not going to respond anyway, is there any need to gather like that and just glare angrily?}

\textit{Aren't they just wasting their time and spoiling their mood?}

That's why she said they had nothing better to do.

...Or at least, there was a time when she thought like that.

"Excuse me, Customer, tonight's reservations have been canceled because an esteemed guest has rented out the entire place."

"What?"

"We shall return your deposit doubled."

Qing received the pouch in a daze.

The reservation fee wasn't insignificant, but it wasn't a large amount either, so even doubled, it didn't feel like a windfall.

"My... My Ultimate Malatang..."

While Qing was dumbfounded, Ziyou stepped forward.

"Look here, there should be a reservation under the name Xin Hui. Has that been canceled too?"

"What? Didn't you hear me? I said an esteemed guest has rented out the entire place."

"Just how esteemed is this guest?"

"It is none other than the Speaking Flower of the Tang Clan. She herself has personally come. Satisfied?"

Ziyou's expression hardened.

Meanwhile, Qing's insides were boiling.

Okay fine. Sure. Cancellations can happen.

Since they said it's an esteemed guest.

After all, how many times had she experienced this uncivilized culture of primitive, barbaric China where even guests were received according to their rank?

But rudeness was a separate matter.

How could she just watch as this server, instead of bowing apologetically, stiffly told them to just take this and get lost?

Right when Qing was about to explode…

"Hey you mo-"

"Do not do that, friend. In Sichuan, it is truly not worth it, especially when it comes to getting involved with the Tang Clan's affairs."

"Tang Clan?"

"The Sichuan Tang Clan of the Five Noble Clans of Zhongyuan."

"Ah. I've heard of them."

She had heard a word or two from Peng Daesan and Namgung Shinjae.

Peng Daesan had described them as persistent and petty bastards, while her Sword Friend said they were the richest family in Sichuan, famous for their poisons.

Peng Guy was a simple man, so his likes and dislikes were clearly visible on his face. Seeing his disgusted expression, Qing thought he must have been in hot waters with the Tang Clan.

That was what Qing thought, who believed her talent in mind reading was unparalleled among the world, at least when it came to expressions.

Anyway, Ziyou's expression as he tried to stop her was so gloomy it looked like something you'd see at a funeral.

Thanks to this, Qing, having missed her chance to get angry, had no choice but to huff and puff as she walked out of the restaurant.

And then, as if it were the most natural thing in the world, she started walking towards the protest site of the canceled customers.

"Look here, Friend, where are you going?"

"I'm going to see just how precious this face is that they can cancel other people's reservations as they please. Why?"

"Didn't you hear them say the Speaking Flower?"

"I know that much, you know? A flower that understands words? Must be a really pretty woman, huh? Then I should at least see her face once."

At this, Ziyou asked as if he couldn't believe what he was hearing.

"You are wearing a sword at your waist and you don't know the Speaking Flower? The Speaking Poison Flower, one of the Five Flowers of Zhongyuan? Friend, are you sure you are a person of Wulin?"