\chapter{A Wicked Woman Eats Malatang (7)}

The kitchen was a horrific sight.

The floor was covered in red liquid, with mangled flesh, chopped bones, and various soft and hard objects scattered about.

The stench was so terrible that everyone reflexively covered their mouths and noses.

Someone with a weak stomach made a faint retching sound.

And the culprit of this disaster shouted while holding a sharp knife:

"It wasn't me! I, I couldn't have done this!"

Qing looked at the scene and thought:

'Why waste all this perfectly good food?'

Malatang oil was all over the floor, with pitiful meat, vegetables, tofu, and noodles floating in it.

Qing snapped in an annoyed voice:

"Hey, what do you mean it wasn't you? Aren't you that so-called Greatest Chef Under Heaven?"

"Yes, I am Bai Changzi, the Greatest Chef Under Heaven. And these are all trash. Why? Why doesn't it taste right? It shouldn't taste like this. What's wrong with it? Is it the stock? No, that's fine. Has the Ma spice changed? No. The tender meat? It's not that either."

The Greatest Chef Under Heaven, Bai Changzi, muttered while darting around with crazed eyes, grabbing ingredients and sniffing them.

"What is it? Everything's fine! Everything's perfectly fine!"

"Look. I get that something's gone wrong, but why are you throwing away perfectly good food? Isn't it a waste?"

Qing still hadn't escaped the memories of scavenging trash for food during her early days in Wulin.

That painful memory she would carry for life continued to fuel her obsession with food.

"No! This isn't fit to eat! It's garbage!"

"No, what? Mister is the one who made it garbage."

"What? I made garbage!? How dare you say that to me, Bai Changzi, the Greatest Chef Under Heaven!"

Qing held out her hand to the side.

Cui Liweng produced Fushen-di from somewhere and placed it in her hand.

Qing's voice that followed was chilling.

"Bai Changzi or Bai Daechang, ah, I want some daechang\footnote{Large intestines}. Anyway, isn't what's scattered on the floor supposed to be my dinner? If you don't give me a satisfactory explanation..."

"No! This isn't my Ultimate Malat, ack!"

WHACK!!! A hearty sound rang out.

This was why people should maintain some of their senses even when they were not in their right mind.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Greatest Chef Under Heaven was in a terrible state.

He rolled on the floor clutching his head, his chef's uniform soaked to the limit with malatang broth.

With his bright red, broth-soaked uniform sticking to his skin, Bai Changzi knelt politely.

"So, what about my dinner?"

"I... I am deeply ashamed. I have no excuse..."

"What? What's the problem? Is it so wrong for me to want to eat a delicious bowl of malatang? I waited exactly forty-five days because they said your cooking was so good."

"That's precisely why. I cannot serve an imperfect dish to guests who came expecting my cooking."

"An imperfect dish?"

"This taste, this isn't the right taste."

Bai Changzi explained the situation.

Originally, the Ultimate Malatang was a high-class dish worth one gold sycee per bowl.

That was why they only used the tenderest loin from young pigs between seven and nine months old, frying the outside before cooking it separately.

The beef was also prepared similarly, using tenderloin from healthy calves.

And for the lotus root, they didn't use just any lotus root, but cultivated a special pond and so on and so forth.

Qing asked incredulously.

"So you're saying you use the best ingredients, cook them separately, and then put them in the broth. But how can it not taste good then? Is a Greatest Chef Under Heaven really necessary if that's the case?"

"Cooking is about considering the condition of the ingredients each day, whether it's humid or not, hot or cold, checking the fat and meat quality, looking at the leaves and shape of vegetables, and bringing out the best taste. Who else but me could gather the best ingredients and pour them into a mere bowl of malatang?"

"A mere bowl of malatang?"

"Although malatang is ultimately just commoner food, there's no high or low in cuisine. In fact, after my Ultimate Malatang, various evolved forms of malatang have appeared, gradually being recognized as a proper dish rather than just a cheap meal replacement."

Earlier he seemed just crazy, but listening to him now, he was unexpectedly a solid and excellent chef.

"But why did you throw away my dinner?"

"Well, you see..."

Today, as always, he had perfectly prepared all the ingredients, putting extra effort into it because of the esteemed guests.

However, the moment the ingredients were combined, a major problem arose in the harmony created by the ingredients and the soup.

He went crazy because even after checking each ingredient individually, he couldn't find anything wrong.

"So, I cannot serve you the dish today."

"Are you serious?"

"Of course. It's such a subtle distortion that no one in the world except someone with my palate as the Greatest Chef Under Heaven would notice, but it's definitely not a proper dish. Um... are you going to hit me?"

"Yep."

Qing nodded, holding Fushen-di.

Bai Changzi explained with a solemn expression.

"Even if I'm hit, my determination to always serve the best cuisine will not waver."

"Craftsmanship is good and all, but shouldn't you know when to stop? Aren't you thinking about the hungry customers waiting outside?"

"Taste is power. For the best cuisine, of course, a time of eager waiting is nece- Ack!"

WHACK! Bai Changzi rolled on the floor again.

Still, in recognition of his spirit, it was a controlled strike with just about one exclamation mark's worth of force.

Qing turned away from the rolling Bai Changzi.

"It looks like dinner is ruined. Damnit, I'm starving to death... Friend, where were we going earlier?"

"Seems we just wasted time. But we got a good show. Say, do you enjoy duck? While not as good as Beijing, Sichuan duck has its own flavor."

"Oooh, that sounds good, huh?"

Qing had already forgotten about the malatang and was chattering away.

After all, didn't he say it was comparable to Beijing duck, even if not quite as good?

Even before her journey into Wulin, Beijing duck, also known as Peking duck, was world-renowned, but she hadn't had the chance to try the original since her journey began.

"Sichuan duck. I'm really looking forward to it."

"That's right. Duck is an excellent dinner. According to the Inner Canon of the Yellow Emperor\footnote{黄帝内经/ Huangdi Neijing}, duck nourishes Qi and builds the body. It's an ingredient martial artists should love."

Peng Chaolei naturally joined the conversation.

"W-Wait a moment! Hasn't the situation somehow naturally turned into that weakling treating us? Sister, I was determined to treat you to dinner today."

"But isn't roast duck much better than malatang? I didn't really like it that much to begin with."

Peng Chaolei answered while scratching the back of her head.

Tang Lan-ah quickly replied.

"We, we have plenty of duck in the Tang Clan too. We even raise them on sulfur."

"Oh. Sulfur duck. Right. According to the Inner Canon of the Yellow Emperor, humans originally can't swallow sulfur, but if you feed it to ducks and let it settle in them, when eaten later, it strengthens bones and nourishes joints."

Sulfur and saltpeter were items controlled by the government.

Not only were they not cheap, but it was impossible to purchase large quantities in the first place.

So feeding expensive sulfur to mere ducks was like feeding gold to dogs.

Of course, the Tang Clan had both power and wealth, so they were capable of doing such.

"I'll properly treat you at our household today, okay? Sisterrr?"

Qing tilted her head.

\textit{Inner Canon of the Yellow Emperor? Is that some kind of gourmet guidebook?}

Qing was just thinking she should get a copy and read it when Peng Chaolei patted her shoulder.

"Qing'er. Let's go. The Tang Clan is offering to treat us."

"Ah. Is that what it was? I didn't think she was including me."

To Qing, Tang Lan-ah felt exactly like a Chihuahua.

After all, she was wagging her tail and fawning on Peng Chaolei, but baring her teeth at Qing from within her arms.

That's how Tang Lan-ah looked to her, overlapping with that contemptible yet cute dog breed.

"Ah, Sister. Wait a moment. I..."

"Our Qing'er's allocation in the hierarchy is near unparalleled. How could they not invite the named disciple of the Godmother? Even if they did, how could you go along? By the way, Lan-ah, what's wrong?"

Qing's allocation put her as a great elder of Daoism.

If they excluded her from a dinner invitation while she was present, it would be tantamount to a declaration of war, trampling on the face of all Daoist sects.

If Peng Chaolei went along happily, she would only be participating in that.

The quick-witted Tang Lan-ah hurriedly changed her words.

"Ah, he, hehe, it's nothing..."

Of course, she didn't forget to think of various poisons at the same time.

\textit{What? A mere veiled woman has such a good background?}

\textit{Then it would be a big problem if I'm caught using poison, wouldn't it?}

And then, immediately she thought:

\textit{Then I just need to not get caught, right?}

\textit{What poisons can I use secretly?}

\textit{I'll have to combine a few with Split Poisons.}

Split Poisons referred to substances that weren't poisonous individually but showed their effects when combined.

For example, putting one poison in the soup and applying the other to the side dishes or personal utensils that are dipped separately.

A poisonous glint appeared in Tang Lan-ah's eyes.

\textit{Arrogant veiled woman!}

\textit{Tonight, you won't be able to leave the toilet.}

‘Even if I'm caught, I can solve it with one use of my ultimate secret technique, Tears of Flowers Filling the Sky', was what she thought.

As Tang Lan-ah was plotting such an incomparably wicked scheme and raising her Poison Qi, Peng Chaolei said just one thing.

"This girl. How frivolous."

Qing brightened up.

"Then, shall we? Friend, come with us too? When else would we get to enjoy the hospitality of one of the Five Noble Clans?"

"This, I mean, are you talking about me?"

Ziyou suddenly burst into laughter and continued:

"That does sound good. The hospitality of the Tang Clan. I've been thinking I should experience it at least once."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Tang Clan received unexpected guests that day.

The daughter who went out to have dinner with her future sister-in-law, Female Xiang Ji Peng Chaolei, came back not only without having dinner but also with a bunch of hangers-on.

Thanks to this, even the Tang Clan Lord had to come out to entertain unexpected guests.

Wasn't she a named disciple of that Godmother, after all?

Although still young, she was at least of an allocation where the Clan Lord should show his face once.

But not to the extent of visiting her personally, of course.

They should come to pay their respects; it was not to the point where the Tang Clan Lord would go to receive them.

So he had called them just to see their faces.

And so the door opened.

The Tang Clan Lord, who had been lying down half-heartedly, sprang up as if flicked.