\chapter{A Wicked Woman Eats Malatang (5)}

The situation had reached a level that the individual Tang Clan warrior could no longer handle.

Naturally, someone higher up had to rush out.

Qing saw a man who hurriedly appeared, using a footwork that almost seemed like rolling on the ground.

In fact, Qing had already had her fun.

Despite everything, the martial artists of the Sichuan Tang Clan weren't evil people.

They had acted arrogantly and tyrannically, thus suffering great humiliation, so wouldn't they at least pretend to restrain themselves from now on?

Even in Qing's homeland, when power abuse became widely known, they would at least pretend to be self-reflective for a while.

So if they added a polite apology at this point, she was willing to forgive them magnanimously like a great person.

However, the Tang Clan had already been standing tall as the kings of Sichuan since the time of the Celestial Martial Emperor.

When one's nose is pointed towards the sky, no matter how much they lower their eyes, they can't see the ground.

The man threw something swiftly.

Thud. Something heavy fell in front of Qing.

It was a whole ingot of gold.

"Enough with the commotion. That should be sufficient compensation for your grievance."

Qing's eyes took in the ever so yellow gold ingot.

She had already caused all the embarrassment she could, so wouldn't this be getting practical benefits on top of that?

Qing, still lying down, slowly reached out and picked up the gold ingot.

Gold was inherently a heavy metal.

As the weight settled in her arms, Qing's anger also melted away.

Indeed, one ingot of pure gold conveyed true sincerity better than a hundred apologies.

So the commotion should have ended here.

If only the man hadn't opened his mouth.

"Just look at that! In the end, it was all a ploy to extort some money. The Tang Clan has bestowed gold despite suffering this humiliation, so who is truly the wronged party in this affair?"

It was the man's strategy to win over public opinion.

He had turned Qing from an unfairly wronged victim into a shameless scammer who tried to extort gold by creating a false pretext.

Naturally, Qing felt wronged.

While the self-harm and extortion were true, she hadn't thought about the gold.

But in a world where even cousins feel jealous when their relatives buy land, the onlookers' gazes immediately turned cold when they saw her take a whole ingot of gold just for causing a bit of commotion.

"Consider yourself lucky. It's only because an esteemed guest is present that we're trying to avoid bloodshed. If not for that, you would have melted into a handful of poisonous water. When you go back, offer thanks to your ancestors."

He didn't forget to add a warning either.

There was no guarantee that a second or third Qing wouldn't appear if they showed weakness.

The man's handling of the situation was quite clean and excellent in its own way.

He had turned the victim into a scammer, shown generosity by bestowing just one ingot of gold, and prevented recurrence through a warning.

The only problem was that it was now that being's turn to step up again.

As the 'even greater' Sun Tzu had said again, again, and again,'"If you do not know the enemy, even the wisest plan becomes an act of retardation'.

\textit{Fucking hell, these cunts. I was going to let it go nicely, but they're seriously going to cross the line like this?}

Qing poked Cui Liweng's side repeatedly.

Then a voice full of anger stopped the man who was turning around.

"Melt into a handful of poisonous water, you say? Very well. Let's see you try it. A member of one of the Five Noble Clans, a prestigious orthodox sect, acting so shamelessly in the witness of all under heaven. Is this the way of the Tang Clan?"

The man stopped in his tracks.

"Look here, old man. Your bravado is admirable, but you should know your place and situation. How dare you, in the middle of Chengdu-"

"Even a mere low-ranking member is so arrogant. I can imagine what the rest of the Tang bastards are like without even seeing them."

At this point, it was clearly an invitation to fight.

The man understood this implication as well.

"I tried to be nice, but it seems that won't work. You fools who only understand when you see blood-"

The man couldn't finish his sentence.

This was because Cui Liweng had raised a sphere made of gathered starlight above his palm.

It was a peerless skill that every martial artist dreamed of.

Its name: Force Compression.

Of course, it wasn't an incredibly rare skill.

Any Master around the Unrestrained Realm could use it.

Only then did Qing reach out, pretending to stop him.

"Gramps, stop it. That's going too far. Are you planning to kill everyone?"

"Then, should I just let such insolent words slide?"

"But if you kill them all, wouldn't you find them way too pitiful?"

Cui Liweng slowly withdrew the Force Compression.

"Hmph, hmph. With such a soft heart. How will you survive in the cruel world of Wulin? Hmph. You. Consider yourself lucky."

In fact, even with Force Compression, Cui Liweng's Inner Force was barely First-Rate, so he would have no Qi left after using it just once.

The man was pale and bloodless.

He hadn't noticed before because his nose was too high in the air to look at others, but now he saw that the light in the old man's eyes was undoubtedly that of a great elder from Buddhism or Daoism.

"I-I didn't realize I was in the presence of such an esteemed..."

"Forget it. I'm just dying to know how noble a person must be to kick away our old man's rice bowl and chase us out of a restaurant."

"That is..."

"What are you doing? After causing all this trouble, are you just going to happily eat your meal?"

"P-Please wait a moment!"

The man hurriedly ran into the restaurant.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tang Lan-ah\footnote{唐蘭啊, lit. 'Tang's orchid'. Dang Nan-a(당난아) in the original text}, one of the Five Flowers of Zhongyuan known as the Speaking Poison Flower, a flower of the Tang Clan and the most beautiful woman in Sichuan, was currently spending a very important time.

She was in the middle of trying to curry favor with her future sister-in-law, or in Zhongyuan terms, daego.

Peng Chaolei was a famous figure in many ways.

She was known as a muscle maniac obsessed with strength, had peculiar speech and behavior claiming she was married to her dadao and calling herself Mrs. Dadao, and possessed an unfeminine tall stature and developed physical beauty, among other things.

Her open-minded personality and straightforwardness were also well-known.

However, these things weren't particularly important to the women of Zhongyuan.

What was important to the women of Zhongyuan was that Peng Chaolei was a comfortable Sister who wouldn't be a competitor when it came to men.

And, above all, she was the sister of that Jade Qilin!

When discussing marriage arrangements in a family, the eldest sister's voice carried truly enormous power.

So Tang Lan-ah was grateful to that unnamed Female Xiang Ji impostor.

After all, Peng Chaolei had come to Sichuan after hearing rumors about her impostor, wanting to see that face for herself.

It was an opportunity to capture the heart of her prospective sister-in-law.

"Hehe, Sister. I'm telling you, this place is really that famous for its cuisine. I'm sure you'll find it to your taste too."

"Well. To build muscle, you need to eat muscle. Hmm, can't we just tear into some meat? Ah. Is there a lot of meat in it?"

"I, I specially ordered them to put in a lot..."

Tang Lan-ah frantically waved her hand under the table.

Fortunately, she saw one of the Tang Clan warriors guarding the interior rushing to the kitchen.

"Really? Thanks for being so thoughtful."

"Hehe. It's nothing. It's food for you to eat, Sister."

"Hmm."

However, it's not easy to keep a conversation going between people with completely different tastes and hobbies.

"Oh my, Sister, your skin is so beautiful. Do you perhaps use any special jade powder or lotus oil?"

"I don't use that stuff. It's bothersome. And it gets sticky when you sweat."

"Ah, I see..."

"..."

"...Ah! Sister, I saw a new craftsman while looking around a workshop the other day! He was a craftsman who could handle gold and silver freely. Would you perhaps be interested?"

"What use is a craftsman who's good with gold and silver? Gold and silver are too soft to be used for weapons."

"Ah, I see..."

"..."

As she was trying to please her (with absolutely no success) and curry favor, that's when it happened.

An urgent Sound Transmission pierced Tang Lan-ah's ear.

-You fool, now is not the time to be leisurely slurping soup. A proper commotion has broken out. Didn't I tell you that Azure Dragon would be too much?

"Ah, Unni. Can I excuse myself for a moment?"

"Huh? Sure."

"Hehe, I'm sorry. I'll be right back!"

Tang Lan-ah hurriedly headed towards one of the private rooms.

"Uncle, what's going on? What could be more important than my marriage prospects right now?"

"There's an elder at the Unrestrained Realm among today's canceled customers. They're quite angry now."

"Why today of all days? Who is it? If it's some Demonic Adept or something..."

"They're clearly an elder from Buddhism or Daoism. They're saying they want to see the face of whoever kicked away their rice bowl and chased them out."

"Oh, for heaven's sake. Why now of all times?"

Tang Lan-ah stamped her feet.

Yes, the noble clans had said they were free from the hierarchy of the Nine Sects and One Union.

That hierarchy was a tradition of the Nine Sects and One Union side, and had no connection with the noble clans who had long established their roots as family groups.

But if you asked if they were really free to not respect it?

Of course not. How could that possibly be the case?

A high-ranking elder meant an elder of a sect, and if you accidentally slighted them, it would be the same as slighting the entire sect.

The reason Peng Daesan and Nan'gong Shencai were comfortable with Qing was that despite their high allocation, they were peers in age, so as long as she wasn't rude, they could remain friends.

That's why only Daoist Changbin, who was a big brother to them and was also basically Qing's disciple's disciple's disciple, suffered alone due to the twisted family(?) tree.

"We can't keep them waiting for long. Hurry."

"I know that too, okay? Ugh, just my luck."

"How do you plan to resolve this?"

A vicious glint entered Tang Lan-ah's eyes.

"What do you mean how? We'll handle it the way we always do."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Friend, what exactly is your identity? And what kind of esteemed person is the old man?"

"Me? Ximen Qing. Gramps? He's the old man who takes care of me."

"That's not what I mean."

"What does it matter? It's not like you approached us because you knew my Gramps was a Master, right? You weren't rude either. Does anything change now that you know?"

"Ooh..."

Ziyou couldn't help but admire.

It meant that by seeing people simply as people and making friends, one could look beyond background and ability to see only the fundamental character.

Not just a unique veiled woman, but perhaps an eccentric sage of Daoism.

In fact, Qing had said it without much thought, just telling him not to worry about it.

After all, she had just gone along with this unknown guy who stuck to her out of boredom, thinking he seemed like another rich young master and figuring she could get a hefty friendship fee.

Of course, she was only accepting such a friendship fee in consideration of his over 400 Righteous Karma Points.

Wasn't this how people normally become friends?

It wasn't like one needed a grand and elaborate backstory to form a connection.

After all, if you hang out for a while and then part ways, it just ends as a brief encounter.

And if there's someone among them who keeps in touch, you might hang out for a long time.

That's when it happened.

A figure came running out of the restaurant entrance like an arrow.

Appearing with red silk clothes fluttering, they immediately knelt down and prostrated themselves in a motion as smooth as flowing water.

Qing admired the graceful apology.

It was clearly not the work of someone who had done this only once or twice.

Do they eat and breathe apologies for a living?

They were truly worthy of being called an apology specialist.

"Esteemed elder, this girl is truly sorry for her disrespect. This girl, in her wicked greed to entertain an honored guest, ended up... hic, sob... What should I do, sob, I'm so sorry, sniff, hic..."

And then, with a beautiful face, they shed tears like chicken droppings, Drip Drip Drip.

Qing admired this sight once again.

\textit{Wow! Crocodile tears for the win! Are these tears the famous 'I'm sorry for whatever' apology videos I've only ever heard about?!}
