\chapter{A Wicked Woman Eats Malatang (4)}

The nature of people is to inherently praise and exalt what is beautiful, becoming endlessly generous in the process.

Look at the incident from the past when Yang Guifei, indulging in playing the villain, wreaked havoc with all sorts of misdeeds, properly ruining the country and even causing a rebellion.

At that time, An Lushan, the rebel leader, couldn't bring himself to behead the Emperor and advised him to get rid of that fishy woman.

(Yang Guifei was also famous for having the worst body odor under the heavens.)

The emperor, unable to smell due to sinusitis, shouted that if she was the most beautiful woman in the world, she could ruin the country a bit. That obviously made sense, right? So why kill the spirit of our beautiful Yang Guifei?

The phrase 'a beauty that can topple a nation' meant that if she was beautiful, one could forgive her even for shaking the country.

Therefore, being generous to beauties could be said to be a characteristic of men.

By the way, if a male friend stubbornly denies this, one should be very careful of their backside.

And Qing was also an inevitable manly man.

"Hmm. Now that I think about it, I guess it's possible they have some kind of company dinner with a guest?"

Qing, who roughly equated the Five Noble Clans to chaebol families, thought that if it was a gathering between chaebol families, they could do it at a famous restaurant.

At that, Ziyou quietly asked a question.

"Don't women usually get jealous when they see a woman more beautiful than themselves?"

"Hey now. Isn't that too much of a stereotypical prejudice? Besides, why are you specifically asking me while looking specifically at me? How would I know that?"

"...?"

Ziyou was at a loss for words.

After all, if you want to ask about women's affairs, shouldn't you ask women? If you ask men, won't you both just end up spreading your wings of imagination?

Then, suddenly.

"I misspoke. I shall sincerely apologize, so please do not take it to heart too much."

He was apologizing with a polite attitude.

In fact, the mystical veiled beauty in Zhongyuan is a fantasy that only exists in stories.

This was because a woman's beauty was considered a virtue to be boasted about to the world, so they didn't particularly hide it.

A woman who hid her face naturally had a reason to do so.

If she was called a veiled woman, it meant her facial features were so extraordinary that ordinary people couldn't handle it, so it was out of consideration that she hid it.

This was Zhongyuan' conclusion about veiled women.

In other words, it was an apology saying, 'Sorry for pointing out that you're ugly'.

"Your speech."

"That was intentional. It means my apology is that sincere."

"Oh really? Then, since you're so sorry, want to treat me to dinner? There must be other delicious things besides malatang, right?"

"Sounds good. Actually, even if they say malatang is the Ultimate, it's just malatang, isn't it? It lacks foundation."

Malatang originated from maocai, a meal for the lowest class of commoners.

About half of the Sichuan people didn't acknowledge malatang as cuisine, saying it was just a meal, not a dish.

Of course, the Ultimate Malatang was an exception.

Still, everyone lamented that if the Greatest Chef Under Heaven made other dishes, they would be much more delicious, but he was just fiddling with mere malatang.

"Today, my friend, you will thoroughly understand why Sichuan cuisine is synonymous with the greatest under heaven."

"Alright. Good, good. Today is a day to eat until my stomach bursts. By the way, I eat a lot, you know? If you think you can't handle it, feel free to declare defeat and stop the meal at any time. You might need to show some teary-eyed pleading, though."

"There's no need to worry about me."

Qing grinned and then asked.

"By the way, do guests usually enter first? Is this Sichuan-style hospitality?"

"How could that be? The more esteemed the guest, the more carefully they should be prepared for and escorted in with the whole family."

"Then is Female Xiang Ji not a very esteemed guest?"

"That can't be the case."

"Then, why?"

Qing pointed at the Azure Dragon restaurant.

After the two women slipped in, the coachmen and other hangers-on stood guard in front of the restaurant.

The large 'Tang' characters emblazoned across their martial uniforms looked quite tacky.

"I thought when they said they rented out the whole place, the whole family would be having a nice meal out together."

"My friend, you have an overtly naive side, don't you? Obviously, they rented it out because they wanted to dine alone."

"What?"

Qing stopped in her tracks.

\textit{They kicked out all those customers just so the two of them could eat alone?}

\textit{What kind of world-class fuckery, what kind of ill-mannered rude bullshit is this?}

Then she took a moment to assess the situation.

That's right.

Qing always assessed the situation.

She wasn't a reckless fighter, and while she occasionally showed symptoms of anger management issues... that was unavoidable due to her mind being messed up by the Heavenly Slaughtering Star and Demonic Arts.

Even in Luoyang, when dealing with the Black Whatever Sect(?), didn't she admit defeat like a man and retreat?

Qing was basically a cowardly type who followed the principle of 'strong against the weak, weak against the strong', and a timid scaredy-cat who never charged in first unless she was certain.

And so, she quickly came to a conclusion.

Qing turned around and headed towards the restaurant entrance.

"Friend, where are you... No wait, what strength is..."

Ziyou couldn't quite grab her hand and only managed to catch her sleeve, but ended up being dragged along.

This was because Qing's pure strength had already surpassed that of Xiang Yu in his prime, and Ziyou was originally the weakest among men without any martial arts.

"Halt. What business do you have?"

Qing looked at the Tang Clan warrior blocking her way.

The martial uniform looked expensive, but the large green 'Tang' character emblazoned in a circle from chest to belly was incredibly tacky.

Since they put one character on the front and back, does that make it 'Tang Tang'?

Even the jackets of prestigious universities don't have such blatantly large emblems.

Qing took a deep breath.

And then she screamed, almost like a shriek.

"ISN'T THIS! SERIOUSLY! GOING! TOO FARRRRRRR!!!"

It was already a place crowded with onlookers.

The canceled customers pretended to disperse but only changed the density of their crowd, still hoping to see the Speaking Poison Flower's face.

Add to that the group that had flocked to see the Speaking Poison Flower following the carriage, and while it might not have reached the level of the Jade Qilin, it was at least a third of that.

It was a shrill, high-pitched scream unique to women.

People who were about to go back to their business after seeing the Speaking Poison Flower, thinking 'Wow! Her beauty is really out of this world', turned their heads to look at Qing and naturally rewound time back to their original positions.

"Does being from the Tang Clan mean you can just cancel other people's reservations? I waited forty-five days for this moment, and just because one young lady has arrived, we're told to get lost? Should we just sink into the ground? Why don't you just tell us to dig our graves and get in?"

"You wench, how dare y-"

"How dare I!? How dare I!? Yeah, okay! Is that how you want to play?! So you mean that you, the great Sichuan Tang Clan people, are so noble that lowly worms like us shouldn't dare!! Dare!!! To talk back no matter what happens to us, right? Oh my, oh my! Look here, neighbors! Look at what they're saying here!!! Look everyone! The oh so noble Tang Clan royalty has arrived!!!"

Qing screamed at the top of her lungs for everyone to hear.

"L-Lower your voice."

"My Gramp's dying wish was to taste that one bowl of malatang he barely managed to eat once when times were really tough, saving penny by penny. I finally got a reservation and brought him here, but..."

Cui Liweng's expression changed into one of subtle discomfort.

Cui Liweng, who had walked the path of a Prestigious Demonic Path in the Heavenly Demon Divine Cult, had never lived in poverty even once in his life.

"Gramps!! I'm sorry!! I'm sorry for being a worthless worm with no backing and no skills!! What can I do when the Tang Clan's young lady is tired of good food and needs to experience commoner food!!"

The onlookers, who were initially just curious, gradually began to murmur with an ominous tone.

Among people living in Sichuan, especially those living in Chengdu, who hadn't experienced the tyranny of the Tang Clan at least once?

Even nameless warriors from branch families, not direct descendants, acted like high-ranking officials just by wearing clothes with the Tang character.

"Ah! What blasphemy have I! O' noble warrior! This madwoman dared to defy the Great Tang Clan, the Greatest Under Heaven, the imperial lords! In Sichuan, the Tang Clan is practically the imperial family and the law, they say! You must not doubt my loyalty! Long live the Tang Clan! Long live! No wait, since there's a heaven above heaven, then the Tang Clan is undoubtedly above the emperor! Long fuc-, I mean, long live the Tang Clan! For ten thousand years! No, eighteen thousand years!! Motherfu-, I mean, eighteen thousand years!!!"

The Tang Clan warrior's face turned pale.

In reality, the influence of the Sichuan Tang Clan in Chengdu had long surpassed that of the royal family.

Even though, hypothetically, the royal prefecture of a Grand Prince was on the outskirts of Chengdu and owned most of the land in Chengdu, they were in a situation where they couldn't exert power due to the Tang Clan.

Moreover, a Grand Prince was a title given to the legitimate line of the imperial family, even among the many princes. Roughly speaking, it was given to the emperor's sons and brothers, even disregarding complicated circumstances.

In fact, it was almost an open secret that the Tang Clan privately said among themselves, 'Even the Grand Prince is no match for us', looking down on and belittling him.

"No! What are mere numbers! How can the greatness of the Tang Clan be expressed in numbers! Please accept this humble one's loyalty! A generation of Tang! A generation of Tang! A generation of Tang Tang!"

However, an open secret also meant an unwritten rule that it shouldn't be said openly.

In fact, among the onlookers, there were also those with particularly tacky attire with single characters like Byeong, Yong, Jol, A, Yeok, Po, Noe, Se, Go, Yeom, Joong emblazoned on them, indicating they were government officials receiving salaries from the authorities.

This was the moment when the story they would talk about tonight was being decided.

"That, uh, please, just shut u-"

"Ah! Shut up, you say!! Are you saying that this lowly being, not even as bright as a firefly under the sun that is the great Sichuan Tang Clan, still lacks volume in her voice!!! LONG LIVE THE TANG CLAN!!!!! FOR EIGHTEEN THOUSAND YEARS!!!! LONG LIVE THE TANG CLAN!!! KYAAAAAAAAAH!!!"

Qing's breathing was already trained by the Fushen-di, making it superior even among Masters.

Her voice was so loud that, with a bit of exaggeration, it seemed like buildings were shaking and the earth was vibrating along with it.

"No, just-"

Feeling that this couldn't go on, the Tang Clan warrior reached out towards Qing.

He thought he should at least pull her away, as she was clearly causing a scene intentionally and couldn't be left alone like this.

It wasn't a wrong judgment.

The problem was that this was the moment Qing had been waiting for and aiming at.

"KYAAAAAAAAAAH!!!"

Qing flew as if hit by an iron cavalry (cataphract).

Moreover, she bounced twice on the ground, rolled over, and sprawled out, looking to anyone like she had taken a hit from a Master, peerless under the heavens.

Qing curled up and trembled like a seriously ill patient.

While rolling, she secretly flicked a small stone, which hit Cui Liweng, who immediately caught on and rushed to Qing.

"Oh my! Child! Come to your senses! How can there be such a law in this world!! This fragile child who's barely twenty!! What mortal sin has she committed by raising her voice a bit!! Is there such a law under heaven!! How can this be the behavior of a prestigious orthodox sect!!"

While Cui Liweng's Inner Arts was barely First-Rate, his Enlightenment had already entered the Unrestrained Realm.

At the Unrestrained Realm, one could freely handle the subtleties of the lion's roar, commonly known as 'YOU DARE!!!', so the old man's sorrowful voice resonated loudly.

A fragile child of twenty.

Fathers with children were greatly moved, and whispers spread among the crowd such as:

'Isn't this too much even for the Tang Clan?'

'It seems they've been working behind the scenes sneakily, and now they're planning to openly act tyrannically.'

'We should warn our children sternly', and so on.

Watching this scene, Ziyou shook his head.

Rather than drawing a sword and charging in, was she seriously trying to gather people and blatantly throw away all concepts of pride and conscience in the gutter?

There had never been such a vicious person in the world.