\chapter{The Plague Ghost Hides Her Power (6)}

Master Zhang clicks his tongue in disapproval.

"Everyone's making such a fuss about dealing with the Plague Ghost. Master Kang, is there really no way? Is that woman really such a master?"

"She's not a master. She's about my level or maybe just slightly stronger."

"And yet?"

The unspoken question was: Then why did you lose?

And with so many men at your disposal no less.

Master Kang wore an aggrieved expression.

"It's a compatibility issue. There's a martial art called the Ground Art Fist. It involves fighting on all fours scurrying across the ground. Even at the same level, it's extremely tricky to counter…"

"If it's such a powerful martial art why isn't it famous? No wait, who in their right mind would learn something like that crawling around on all fours?"

"Exactly."

"Hmm."

Master Zhang stroked his beard.

Truthfully there was a way to drive out the Plague Ghost.

He could go to the city and hire a sword-for-hire—, or a wandering martial artist. With Master Zhang's wealth it wouldn't be too difficult.

"Everyone's clamoring for me to invite a master from the inner regions but those fools don't realize how dangerous that would be."

If they couldn't handle the Plague Ghost what would happen if they brought in a master who could defeat her only for that master to settle down in the village?

Someone like Master Kang was the perfect balance—someone they could coexist with.

Bringing in a true master might mean handing over Jianping entirely.

Master Zhang cleared his throat.

"So in a way the Plague Ghost is one of our own, isn't she? And she probably doesn't want to keep living as a beggar. Maybe we can reason with her. After all she's still a martial artist, it's not like just anyone can step up to her."

In other words: You go and try to persuade her.

From Master Kang's perspective this wasn't a bad idea.

He knew his own limits. As a Second-Rate martial artist, where else would he get treated like a master if not here?

If they brought in someone stronger from the mainland?

He'd be out of a job.

But the Plague Ghost? He was confident he could defeat her once he got used to her Ground Art Fist.

The thought that she might be a once-in-a-generation master never even crossed his mind.

And why would it?

A First-Rate master would be radiating Qi, but the Plague Ghost showed no such signs.

Above all, how could such a master behave in such an ugly and shameful manner, with no sense of dignity to be found?

Master Zhang's face brightened.

It was a difficult topic to brought up, as he'd been worried about offending a martial artist's pride, but if Master Kang was willing to step up so readily. all the better.

"You're the only one I can rely on. Master Kang. Go and talk some sense into her will you?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's businesses in Jianping were nearly settled.

Except for one thing.

"Food! Now!"

"Y-Yes! Right away!"

"What? Are you rebelling now? Didn't get beaten enough? How are you supposed to address this person?"

"Oh Great and Mighty Beggar Lord!"

"That's more like it."

Qing nodded in satisfaction then propped her feet up on the table and leaned back in her chair.

If her homeland's folks saw this, they'd be furious and ask, 'What kind of rude thing is this, putting your feet on the table while eating?'

But to the people of Zhongyuan?

They'd be angry just the same.

The dining table was sacred.

And here she was in the middle of a tavern making a spectacle of herself.

To make matters worse she wasn't even in her guise as the Heavenly Blossom Sword but as the revered Beggar Lord of Jianping's Wulin.

A beggar.

This beggar woman had taken the most visible spot in the tavern.

'Why is she sitting down with her feet up on the table, showing off her bare, filthy feet?'

Any customer who walked in would turn right back around.

What kind of tavern owner would let this happen?

But the owner was right beside her kneeling.

Qing patted his smooth bald head.

"I've been thinking."

"Y-Yes! Speak O Beggar Lord!"

"Once there was this really stingy tavern owner. A thriving place like this must produce at least a full barrel of food scraps every day, right?"

The business that produced the most of food waste, what people called scraps, were taverns.

The hospitality culture of Zhongyuans was based on pretense, so there wass a very strange culture where if someone who has received a meal scraped it clean and ate it all without holding back, the person who bought the meal feels embarrassed.

If there is no leftover food, it means that there is not enough food, so the host was being miser and leaving guest hungry or something like that.

This was especially true in high-end taverns where customers always left food behind.

"But instead of giving it away, he'd let it rot for days before tossing it out. Why? Did he hate seeing beggars enjoy good food?"

"Ha ha ha…"

The owner laughed awkwardly.

Qing pretended to ponder.

"Then one day even the rotten scraps stopped appearing. Did he start feeding pigs instead?"

"Ha… ha ha…"

"Using leftovers as pig feed is actually a great idea. What's the point of leaving food behind? Throwing it away will just stink, attract bugs, and pollute the environment. And you get to raise pigs too. Two birds with one stone. Perfect, isn't it?'

"Y-Yes O Beggar Lord."

Qing idly stroked the owner's bald head then suddenly flicked her wrist!

"But using that as an excuse to hoard scraps is a bit much, don't you think? Turns out for every ten piglets the Zhang family's pigs birthed, he only got one in return?"

"Ha ha…"

"So where did the missing scraps go? Did some heartless owner dump them in the river just to spite the beggars?"

"Ha ha ha…"

"If he left it alone, the beggars would have scraped it clean, and a simple sprinkle of water would have cleaned it up. But he went all out, carrying that heavy bucket downstream and letting it float away? Why did he do that? Did he hate the sight of those beggars who didn't even work and just played around eating for free? Did he hate giving away his trash, which he had to throw away anyway, to the point where he had to hire someone to throw it away?"

"Ha ha ha…"

"Why are you sweating? Are you ill or something?"

"N-No O Beggar Lord."

"Hmm. Well, I do get it. I've met plenty—no lots—of people like that even in Zhongyuan. Shopkeepers who think giving customers even a little extra was a huge loss. And beggars? They must've really disgusted him."

Even in Qing's more commercially advanced homeland, such shopkeepers existed.

In this less civilized era it was even worse.

It wasn't about loss, just petty spite.

Rather than a loss, they just didn't want the customer to benefit.

The thought of a beggar, not even a paying customer, benefiting from their scraps was unbearable.

"But what happened to the beggars who relied on those scraps?"

In a place like Jianping where compassion was already scarce, losing their main food source was devastating.

As the weak beggars started to starve to death, the already vicious beggars evolved into hungry beggars and became extremely vicious

"Why aren't you answering? If you've got nothing to say, what's the rule?"

"H-Ha ha ha…"

"That's right. Laughing brings good fortune.'

Qing patted the owner's bald head.

"Though honestly, it's not like he did anything wrong right? A tavern owner can do whatever he wants with his scraps; feed pigs, dump them, even eat them himself. It's not a crime or evil, right?"

"Y-Yes O Beggar Lord."

"Hmm. Yeah. Right. Exactly."

Had the owner committed a crime?

No. It was just petty spite.

There were quite a few beggars who died from that petty spite, but those were just beggars killing other beggars to secure their own rice bowls.

But that wasn't the owner's fault.

So Qing would repay him in kind, with equally petty spite.

It wasn't like shutting down Jianping's top tavern for a few days would ruin him.

But it was a lesson: If you went out of your way to screw others, you too would suffer the same fate.

Qing let her arm dangled.

From the kitchen, came the clatter of pots and pans, and the salty greasy aroma of Zhongyuan cuisine.

A moment later…

"…I've been thinking."

"Speak O Beggar Lord."

"Once there was this really stingy tavern owner…"

\textit{How many times had I heard this now?!}

\textit{The same story, word for word over and over and over, with no single deviation.}

\textit{Enough to make my ears bleed.}

The tavern owner clenched his eyes shut.

\textit{I wasn't trying to take out the trash can!}

\textit{No, before that, I should have put rat poison in the trash can and completely killed those beggars!}

Of course, as Qing often argued, regret was never repentance.

Repentance must be about realizing one's own fault and deeply regretting it.

Regret was nothing more than the bitter feeling after you've been screwed over, or in other words, after it was too late.

Still.

Jianping Pavillion wasn't actually ruined.

Qing had only planned to torment the owner for a few days before leaving.

A few days of lost business wouldn't bankrupt or kill him.

Just petty revenge.

But the owner didn't know that.

\textit{This witch isn't just ruining my business, she's going to kill me!}

There was only one hope for the owner.

That Master Zhang would bring in a real master to deal with this monstrous beggar.

He just had to endure until then!

…Or so he thought.

"Ahem. Beggar Lord."

Instructor Kang slumped into a chair across from Qing.

"Hmm? What? A rematch? I don't mind, but have you eaten? Did you eat before you left? The food will be ready soon. Since it's a pre-fight meal, let's eat together?"

"No, it's not that. Ahem. Let me be direct. Master Zhang is quite impressed by your skill. I've known him for a long time, and I know he's a very generous man, so I'm sure you won't be disappointed with his treatment."

"Ah. Is that so?"

Qing slumped lazily.

"Tell him 'No, thanks'. I've got no business with Master Zhang. If he wanted to reward me he should've done it when I was the Plague Ghost. Let's just go back to ignoring each other, like cows and chickens."

There was no grudge between them.

Not even worth petty revenge.

What dealings could the most powerful man in Jianping have with the weakest beggar?

"Hmm. Well, that's okay too. But if you change your mind, just knock on Master Zhang's door anytime."

From Instructor Kang's perspective, this was a satisfactory outcome.

She wasn't a monster who went mad after learning strange martial arts, she was just a martial artist who had come to avenge a past grudge, even though she was still a beggar back then.

A crazy bitch was terrifying.

It was terrifying because you had no idea what she would do, because she could do anything.

But if her vengeance had a target?

If you haven't incurred that resentment, then there's no reason to be afraid, right?

Instructor Kang glanced around the empty tavern.

The owner of Jianping Pavillion had always hated beggars more than anyone in Jianping.

There was a saying in Wulin: Beware of beggars.

He'd ignored it and now he was paying the price.

A pity, but he'd brought it on himself.

If you're going to hate someone, at least leave no loose ends.

That was Instructor Kang's takeaway.

But the owner's perspective was different.

It was a moment when his heart literally sank and everything went black.

\textit{Master Zang, no, that old fool from Zhang family has no intention of driving out the Plague Ghost!}

\textit{I can't live like this.}

\textit{I have to do something!}

\textit{But what?}

"Ugh, where was I? I forgot because it got cut off midway. Hmm. I guess there's nothing I can do. Well. I've been thinking…"

"Ha ha ha ha ha…"

"That's right, when you laugh, it makes me happy too. So, once there was this really stingy tavern owner…"

The owner steeled himself.

"I have to do something. Now!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The owner was desperate, so desperate he took action.

When you're thirsty, you dig a well.

With even Master Zhang turning a blind eye, his only hope was to grasp at straws himself.

The next morning.

"Where's the owner? Hey, waiter! Where's your boss? Owner, come out! What, not coming out? Are you giving up on business?"

The waiter scurried over and prostrated himself.

"He—he went to the inner regions to place an order, O Beggar Lord."

"An order? For what?"

The Mongol raiders would soon arrive to plunder (collect tribute).

Some of the loot items couldn't be sourced locally, so someone had to go to the inner regions to procure them.

So Jianping sent people periodically to purchase items that are to be plundered.

And today was the day.

"He said, he said he wanted to offer the Beggar Lord the finest delicacies so he went to order premium ingredients."

It was nonsense that anyone who heard it would find absurd.

Qing's brow furrowed.

In other words?

"That bastard ran away?"

\textit{I planned to leave tomorrow, so three days of disruption was not that bad.}

\textit{But after just one day of torment, he'd fled?}

\textit{This guy's adding to his crimes.}

If the owner had known Qing plans, he'd have been furious.

If he'd known he only had to endure for three days, he wouldn't have forced himself onto the tribute procurement trip.

But Qing had never intended to tell him.

Why ruin the fun?

So the owner's suffering was entirely self-inflicted.

And where was he now?

"Help! Please, noble martial heroes! Listen to me! A bandit has taken over my home and was trying to kill us! Have mercy!'"

In the square of Zhaoyang County, the owner and his family knelt wailing for help.

If Qing had seen this, she'd have scoffed, 'Is this the best solution you could come up with?'

But to the city folk, this wasn't an unusual sight.

Country bumpkins often came to the city begging for help from the chivalrous heroes of legend.

It happened several times a year.

Because in their stories, heroes never turned away the weak and helpless.

Of course the outcome was almost always the same.

Most realized that Wulin was cruel and the heroes of legend were just that—legends.

Nine times out of ten, no, ninety-nine times out of hundred, they went home disappointed.

But very rarely, things turned out differently.

The very lucky might meet a real hero, or a kind-hearted martial artist, or even a bored master.

Like now.

"Ahem. What seems to be the trouble?"

A noble figure in expensive martial robes, a gleaming golden sword at his waist.

A hero straight out of legend.

\textit{Heaven has answered my prayers!}

Tears streamed down the owner's face.

If Qing had seen this she'd have been baffled, 'Why would heaven help someone like you?'

But regardless, it had happened.
