\chapter{The Plague Ghost Hides Her Power (7)}

"Ah, Great Hero! That villain's atrocities have gone too far!"

"Great Hero…! Huh, ahem."

"Yes, Great Hero! That villain has been roaming the village, raiding homes and stealing all the food. In this already harsh winter, such heinous acts are unforgivable!"

The tavern owner's eyes reddened.

"Even when we begged them to spare food for the children, they flipped the children's bowls and trampled them under their filthy feet, laughing cruelly! Such a monstrous villain!"

"What?! How could someone so wicked exist?!"

"And that's not all! Despite the kindness our village showed them, they repays us with such ingratitude! How dare they…!"

"Kindness you say?"

"That villain was once a beggar who lived off our village's generosity. But after disappearing for a while and learning martial arts, they returned, forgetting all favors and now wreaks havoc against us…"

The tavern owner's voice trembled with emotion.

"Great Hero, how could I, a small-scale restaurant owner, only serve leftovers for a day or two? Even though I didn't intend to give them to beggars, there are more than a few beggars who have lived thanks to me. And yet this is how they repay me…?"

He couldn't continue.

His face was flushed with anger and tears welled up in his eyes threatening to spill over.

It was an expression of genuine resentment.

This wasn't an act.

He genuinely believed he had been wronged.

Human memory was a fickle thing often rewritten to suit one's narrative.

Of course if Qing had heard this, she would've been so outraged her fists would've moved on their own.

But Qing wasn't here. Instead there was only a righteous hero witnessing the plight of an oppressed man.

"How shameless! This is too much!"

Naturally the hero was furious.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had only intended to teach the tavern owner a lesson, but his escape left her with time to kill.

The people of Jianping seemed to have sworn off meat entirely, no matter where she wandered there wasn't a whiff of it.

She could've just left Jianping and continued her journey to Mount Changbai but…

\textit{How can I leave when that bastard ran away?}

\textit{If he comes back and finds me gone, he'll think he outsmarted me!}

\textit{I can't let that slide.}

So there she was sprawled dramatically across the large circular dining table in the tavern's center.

To call it sprawled was an understatement.

Her limbs splayed out, her head and knees dangling off the table's edge.

Her head was hanging out, her long hair trailed on the floor, while her legs swung idly in the air.

Even if your legs are originally designed to bend like that, wouldn't it hurt if you tilted your neck like that?

But Qing's physique was beyond human limits, and her cervical bones and neck muscles were also of a strength beyond human.

Her head was also unusually light making the pose effortless.

As she lay there staring upside-down at the tavern's entrance, the owner suddenly burst in parting the beaded curtain with a dramatic flourish.

Then, he stood upside down with his feet on the floor of tavern in the sky, and pointed accusingly at her, his face a mix of fear and triumph.

A sigh subtly subtly escaped from Qing's mouth.

\textit{What the heck? Is he crazy? Where did that come from?}

"Great Hero! Look! That's the one! The one lounging on the table like… like…!"

The owner called out to someone.

\textit{What? A great hero? Who have you summoned? You said you were going to the mainland, but what is the mainland? Is it some kind of city center?}

Then from behind the curtain a swordsman stepped forward at the upside-down entrance, or rather ducked under it.

For reference, a curtain is a type of screen made of strings with beads or weights strung on them, hung in several directions at the entrance of a store, etc.

People outside the store are usually standing, so the inside of the store is not clearly visible due to the curtains.

Meanwhile, people inside the store will be able to sit and look outside, so they can enjoy the scenery outside under the curtain.

It was a very scientific form of primitive screen.

If you fit under that curtain?

The curtain is usually hung down to reach the forehead, so for someone to pass under it meant they were short.

A tiny hero had arrived!

The moment their eyes met the boy recoiled in shock.

"A-a monster! A real monster!"

"Great Hero! Not a monster, it's the Plague Ghost!"

"A ghost! A ghost!"

"No, not a ghost! The Plague Ghost!"

It was understandable.

Qing was the would-be Divine Thief, a person who has been taught the mystical arts of the Divine Thief, or in other words, the art of thievery.

The face of the ghostly mother with the plague on her face was a grotesque skin-mask.

Qing smiled faintly.

The sight of a head lying down with its neck tilted back, a ghostly face hanging upside down, and a tear in the corner of its mouth was the stuff of nightmares.

"Eek…!"

The poor young hero who'd come to save the day now found himself face-to-face with a horror beyond his worst dreams.

Qing grinned wider, her voice dripping with amusement.

"What the heck kid, pretending not to know me? Surely you haven't forgotten already, have you? Did you forget our secret friendship already?"

"Huh?"

The tiny hero blinked rapidly.

After a moment of hesitation, recognition dawned on his youthful face.

"Ah… is it Beggar Sister?"

"That's right. Flower Beggar Sister."

"Uh… 'flower' is a bit of a stretch…"

"What happened to our secret friendship? Still so stubborn huh? Haven't changed a bit."

"And it wasn't a secret friendship, just a regular one…"

Indeed!

Just as birds listen to what is said during the day and rats listen to what is said at night, this boy is the one who listened to the words of the Murong Family.

A determined soul who could say with certainty that nothing was not true, a flying boy who wandered outside the house secretly at night!

Flower Beggar's secret (and not-so-secret) friend!

Murong Jun, the eldest son of the Murong family!

\textit{But really, this kid was something else.}

\textit{Does he only show up when I looked like a beggar?}

Qing sat up planting her feet firmly on the table.

"Wow, how long has it been? Three years? Four? How old are you now, Jun'er?"

"Twelve!"

"Wow, you've grown so much…not? Jun'er, are they not feeding you at home? It's okay, you can be honest."

"I grew a \textit{cun}!"

"Ooh, impressive… really grown…"

For reference a \textit{chun}\footnote{寸; 1 chun = 3.33 cm} was about the length of a finger joint.

\textit{Three years for one \textit{chun}. At twelve, assuming a long growth spurt of nine years, umm, that'd be three \textit{chun}.}

\textit{Young Lady Murong wouldn't have to worry about her little brother surpassing her in height anytime soon.}

\textit{But Young Lady Murong is also on the small side…}

Qing's gaze softened as she mentally calculated his future stature.

\textit{But growth spurts were unpredictable, it may not be a decided future yet, right}

"So, what brings you here?"

Moyong Jun beamed.

"I ran away from home!"

"Ah. Ran away. Are you that confident?"

"Yeah! Our family says we should always stand tall!"

"Yeah. It’s nice to see you so confident."

Qing bit back a lecture about the dangers of Wulin and how he kept wandering around.

Instead she nodded sympathetically at the man now standing by the entrance as if he was having a hard time.

\textit{Red? Green? Black? Yellow? Blue? White? Anyway, I think it was the bodyguard that used one of the colors as a name, but I don't know, was it red?}

The bodyguard nodded back.

His presence meant the Moyong Clan already knew about the 'runaway'.

They were likely tracking him, leaving markers or checking in periodically.

Besides. who'd dare mess with a well-dressed well-armed young master, escorted by a formidable guard?

"So what's going on?"

"They wouldn't let me go to the Yizheng Martial Study Academy. But my sister got to go! I was left alone, and I wanted to train there too…"

He'd misunderstood her question, answering why he'd run away instead.

\textit{Still, umm, it was a bit harsh.}

\textit{The academy's youth division was more about socializing than serious training.}

\textit{For a clan like the Murong connections will came naturally, so his father must've decided that martial arts training took priority.}

\textit{But for an eleven-year-old (now twelve) it must've been crushing.}

Then suddenly—

Qing's eyes sharpened into a glare locking onto the tavern owner.

The gaze of the tavern owner, who had already been pale, turned blue.

"Eek."

The picture was clear.

While searching for a master to drive out the Plague Ghost, he'd stumbled upon a well-dressed boy with a fancy sword and a bodyguard.

Well, that's what a kid would be like at this age.

A few embellishments about the "evil ghost" and the boy was eager to help.

It would be good to drive away the plague ghost.

He was obviously a good family son, so it would not be surprising that the plague ghost would not dare to speak against him.

\textit{But what if I actually been some deranged monster? What would've happened?}

\textit{Most wouldn't dare touch a noble young master, and if he reveal he is a Murong, it would be een more unlikely.}

\textit{But what if he'd run into a true madman? Or someone with a grudge against the Murong Family?}

\textit{Wait, this idiot didn't even realize Jun'er is Murongng Jun!}

"You little shit—!"

It was the moment when Qing just started growling.

Murong Jun suddenly stood up and blocked the way between the owner and Qing.

Of course, Qing was sitting at the table, and Murong Jun was short, so he couldn't even block her view.

"Wait! You can't bully the weak!"

"Huh?"

"That's not right! Since ancient times, a hero must uphold justice and protect the weak. You can't torment someone who doesn't even know martial arts!"

"Wow. Such noble words from our Jun'er. I'm touched."

"Hehe…"

"But Jun'er, what if this guy, no, this uncle here was beating up an old man? Who would you help then?"

"Uh… the old man of course! But… does that mean the weak can sometimes be strong?"

"Listen. But what if, plot twist, the old man was this uncle's sworn enemy? His parents' killer? Still help the old man?"

"Avenging your parents is filial duty! So… don't help the old man."

"What if the old man wasn't this uncle parent's enemey, but just a thief? He stole money from this tavern and refused to return it? The owner's was beating him to try to get his money back."

"Uh… stealing is wrong and not returning it is worse…"

"But what if the old man stole to save his sick granddaughter? What if he had no choice but to steal the money to save her, or rather, to keep her alive? What if he was desperately holding on because if he gave up the money, his granddaughter would die?"

"W-well… that's too sad. The old man probably couldn’t come up with a lot of money, and he couldn’t just leave his granddaughter to die…"

"But wait—It turns out the owner was also saving up for his wife's medical expenses. If the old man didn't give up the money he stole, she would die without treatment. Then who should you help?"

"I'd… pay the owner back myself—"

"But what if Jun'ah doesn't have money? Our secret friend is rich, but not all swordsmen in the world are rich. Some even say heroes should be poor!"

"Uh…"

Murong Jun's eyes darted in confusion.

Qing smirked pressing further.

"Now, who should you help and who should you save? Shouldn't we help the tavern owner, the original owner of the money? Then, kill the granddaughter? She's poor and sick, so she was destined to die anyway, wasn't she?"

"That's, that's not possible."

"Well then? Help the old man save his granddaughter? Kill the owner's wife? The young granddaughter, with her bright future ahead of her, will live longer. So, it's only right for the older wife to die, right?"

"That, that too…"

Murong Juun trailed off, not knowing what to do.

"That’s just too weird. Then what will Beggar Sister do?"

"Me? I'd storm the doctor's place and threaten him at swordpoint. Just let them both live."

"That's… cheating! You said I couldn't just pay!"

"I'm saying what I'd do. Because I'd know the whole story."

"What if you didn't know before?"

"Then, it's a disaster. 'You scoundrel! How dare a strong man bully a weak old man?! Bullying the weak is unforgivable!' I'd knocked him down in one blow. The old man's granddaughter survived, and the poor owner lost both his money and his wife. I'd be truly proud of myself for doing what a hero should do."

"That's not heroic!"

"Why not?"

"You didn't even ask what happened! The poor owner suffered for nothing!"

\textit{Was the owner even the owner here? Whatever.}

Qing's smirk widened.

"Right. So how long will you keep standing there? Is Flower Beggar Sister too strong to bully a weak tavern owner?"

"Ah!"

Only then Moyong Jun flushed.

He even lowered his head in embarrassment.

\textit{But the kid is sharp, he get my point very quick.}

\textit{When I first met him before, he was a rospective Sex Fiend, but after I explained it to him, he immediately understood and became a new person.}

Behind him, the bodyguard standing at the door bowed respectfully toward Qing.

"Hey you. Headbutt him. Now."

"Y-yes ma'am!"

"Is that how you answer?"

"I'll headbutt him! O Great Beggar Lord!"

And so the tavern owner's true suffering began.