\chapter{The Plague Ghost Hides Her Power (11)}

"[Die!]"

The Mongolian cavalryman charges forward, swinging his crescent blade with immense force.

The trajectory of the crescent blade resembled the symbol for infinity in the Western Regions.

The heavy weapon cleaved through the air with a whoosh-whoosh like a hornet buzzing past one's ears, its ferocity was beyond description.

If Qing dodges to the left or right of the oncoming horse?

The crescent blade will tear her apart!

So she dropped her weapon and bowed her head instead.

Not as a sign of surrender, but as an emergency evasion!

She flattened herself and slipped between the charging horse's front legs.

To be precise, Qing just stood still. The horse simply galloped over her.

Why did Qing usually knelt?

It was for momentum!

The moment the horse's hooves passed, she sprung up with all her might, straightening her back and raising her arms in triumph.

Her back brushes the horse's belly, and with a force greater than the rider's weight, she flips the beast upward.

Hiiiiing!

The horse's cried in panic.

Horses after all were creatures that cannot fly.

Being flipped mid-air was a first in its equine life.

The rider toppled backward, screaming as he crashes to the ground.

At the same time a bizarre battle cry echoed from the left:

"Alralralralralralral—!!"

\textit{No, what kind of battle cry are you showing off?!}

In that moment—

Something light and smooth slithered onto Qing's right arm as she still celebrates.

She turned her head to see a noose tightening around her shoulder.

Following the rope she finds a wrist tightly wrapped with it, then a shoulder, and finally the smug face of a barbarian grinning as if he's finally caught her.

But that was only for a moment.

Qing twisted her wrist, grabbed the rope, and yanked.

A force beyond human imagination pulled the rope, causing the barbarian to flew up and drew a gentle arc toward Qing.

The one being dragged away were the barbarian.

The barbarian's face twisted in shock.

If he weighed over 150 jin, how much strength must it take to drag him so effortlessly—

His thoughts ended there.

Qing leaped up and—smack!

Like a ballgame from her homeland, her left palm smacks the barbarian's forehead.

His head exploded like a watermelon.

But even a dead tiger left its pelt behind, and a barbarian with burst head left his torso

Its wrist was still tightly bound by the rope.

Qing grip the rope with both hands, twisted her waist, and began spinning in place.

The headless corpse acts as a weight, stretching the rope taut.

The rope swept wid,e tangling around the legs of the charging horses.

Hiiiiing! "Ack!" "Gah!" Hiiing!

Horses and riders toppled clockwise one ater another, their screams filling the air.

"Yah!"

Qing released the rope.

The noose slip free, and the headless corpse, now without a center of rotation, was flung away by centrifugal force.

It crashed into a pile of horses and riders, sending them tumbling.

Qing kicked up the zhanmadao she dropped earlier and catched it.

There's still another blade on the ground, but wielding two was just a symbol of defeat. The only attack available was  spinning attacks.

"[This monster! Die!]" "[Diiieee!!]"

"[Eek!]" "[We're going to die! Run!]"

Some barbarians charged with undying resolve, while others turned their horses and flee, abandoning their comrades.

There was an ominous color in Qing's eyes, and her lips were split open with an evil smirk that wouldn't close.

She scanned the numbers above the charging riders.

\textit{Eighty-three, one hundred thirteen, fifty-two, forty-six.}

\textit{Except for one guy, none cross the line, and their overall numbers aren't high.}

\textit{But they must die.}

\textit{Because they don't see people as people.}

\textit{It could be said to be a blind spot of Evil Karma.}

\textit{Evil and Good Karma are just results, they doesn't reflect the person's heart.}

\textit{Of course results can't excuse intent, so even well-meaning actions should bear responsibility if they cause harm.}

\textit{But these barbarians?}

\textit{They see the defenseless, umm, conscience-lacking people of Jianping as livestock to slaughter.}

\textit{They believe they still hold power over Zhongyuan's people, citing past subjugation.}

\textit{They're irredeemable scum, the worst of the worst, doesn't even realize they were committing evil.}

\textit{So, are they even human?}

Qing's eyes darken with a malevolence never before seen.

If someone could read her mind, they might asked 'Who's the one not seeing people as people?'

But at least the Heavenly Execution Star of this era could be justified in saying that it made a clear distinction between humans and beasts.

Qing grinned.

\textit{Hiding my strength is so fun.}

\textit{If I concealed my Qi and pretend to rely on brute force, they think they can win with sheer passion and effort.}

Qing charged forward.

Grabbing a horse's mane, she swung onto its back, creating the image of two people riding the same horse naturally facing each other.

With her left fist, one by one, she lightly knock off the teeth, yellow teeth scattering in the air, and the barbarian, his eyes wide open, naturally tilted to the side and fell off his horse.

"[Brother!]"

A comrade rushed in---whether a sibling or just a friend, it didn't matter.

Qing leapt from the horse's back, severing his neck with a flick of her blade.

"[Sword Force! She's using Sword Force! Be careful!]"

But it was already too late.

Actually, the Mongolian cavalry's skill was at least at First-Rate, Peak Realm, or nearing Transcendence.

There were over thirty of these cavalry, so it was not a force that could be easily dealt with.

But the terrain was perfect.

For them, it's the worst battlefield.

The Mongolian cavalry's infamous 'swarm tactics'—riding, shooting, fleeing, then repeating—once conquered the world.

Later strategists called it the 'locust swarm', referring to the savages who spent more than half their waking lives on horseback, who would band together and disperse, causing such chaos that people would tremble in horror.

Of course, there are many ways to deal with these swarm tactics.

But the outrageous idea of charging straight into the swarm? Unheard of.

Even if they were not heavy cavalry wearing armor, weren't cavalry still cavalry?

Who sent infantry into a cavalry formation?

Surely, if you were going to choose death, there had to be a better way.

But now, it worked.

Why?

Was it the insurmountable gap between mediocre cavalry and elite infantry?

Was it because mediocre remain mediocre even if put on horses, and elites remain elites even on foot?

Of course, there were aspects like that too.

But mostly it was because the Mongol barbarians had set foot in the city, which was a disadvantageous terrain that was no different from a dead end.

Swarm tactics were nearly invincible in open terrain, where they could move in all directions, scattering, grouping, shooting, and stabbing.

But on the contrary, the moment their movement were restricted and blocked on all sides, their combat power drops sharply.

The best way to counter them was to lure them into such restricted space and annihilate them.

The Mongolian barbarians were not unaware of this fact.

But they came to slaughter weak flock, not expecting a battlefield.

They just came to kill anyone bigger than a cartwheel.

Who would have thought such a monster would be lurking around!

Even worse, the biggest problem was that the Mongol cavalry could not use the bow, their most powerful weapon.

Mongolian archery weren't ordinary.

It was a forbidden martial art, a relic of the previous dynasty, outlawed by the current regime.

The great warrior Nain Pureukdeok nocked an arrow, its tip gleaming with starlight, silently aimed at Qing.

It was a skill called gangshi, which meant arrow loaded with Qi

The drawn bowstring hummed with tension.

A vortex of energy swirled around the arrowhead.

If released, it would pierce through anything at blinding speed.

But Nain Pureukdeok only glared at Qing, his eyes full of resentment.

A drop of sweat forms on the tip of his nose, and then quickly fell down.

Even in the harsh March cold of northern Liaoning Province, which was harsher than Zhongyuan's midwinter, sweat formed on the exposed skin, and white steam rose from the skin.

This was proof that it was consuming that much concentration and enormous mental strength.

He watched Qing.

He was constantly measuring her running speed, memorizing her stopping movements, reading her direction of attack, her preferred foot, her preferred movements, and her habits.

He witnessed the tragic end of the dying sons of the prairie, the righteous brothers, and the tribal warriors.

How painful that feel!

The blood vessels in his eyes burst and itturns red, and his teeth grind so hard that pieces of his molars crumbled and rolled around on his tongue.

At the same time, he acknowledged his foe.

Never in his life has he faced someone so unpredictable—instinct and savagery surpassing trained martial arts.

If she had been born as a man of the steppes, she could have been a great Khan.

But no warrior was without habits.

As the slaughter continued, the afterimages of Qing in Nain Pureukdeok's vision dwindled.

As he narrowed down the possibilities for the future movement, the afterimage reduced from three, two, then one.

Finally, a single afterimage that precedes Qing, a future path that was completely determined, came into view.

Nain Pureukdeok aimed ahead.

A trajectory that would lead to the most fatal point in the human body, piercing the delicate skin under the ribs and tearing through the liver, where the enemy pass by in the immediate future.

He took a deep breath.

And then exhaled, while holding his breath for half a breath.

The tremors in his whole body disappeared, and he finally let go of the bowstring-

Fwip.

With a somewhat disappointing sound, the star-lit arrow fell unceremoniously to the ground.

Nain Pureukdeok slowly lowered his head.

A handle of the dagger was stuck in his side, under his ribs, and the hand holding the handle was a man standing next to his horse.

\textit{Was he the man standing behind the young beggar?}

It was Nainporeukdeok's last thought.

The great warrior fell from his horse with a thud.

Qing glanced at the scene.

\textit{Wow, he just killed him like that.}

Of course the barbarian leader's killing intent was palpable, but how could Qing not notice it?

Especially with Awakened Sense.

She pretended not to notice repeating predictable movements to lure him in.

She was also curious to see what kind of archery martial art she was encountering.

She wanted to dodge gracefully and savor his frustration.

\textit{Above all, I wanted to save the strongest for last, but, shit…}

As the thrill was gone, the ominous glint in Qing's eyes disappeared without trace.

All that remains is to beat the remnants without any regrets.

With Warrior Lu who joined in after putting Murong Jun to safety, the remaining barbarians were wiped out in an instant.

Those who could flee already did; the rest were too enraged to think, making them easy prey.

Soon the square was littered with corpses.

\textit{Well, whatever. Still, I'm satisfied. It was fun.}