\chapter{The Plague Ghost Hides Her Power (5)}

Qing slowly stood up.

Then, a collective gasp.

"She stood on two feet!"

"She could stand up properly?"

"What kind of bizarre…!"

\textit{No, of course, I stands on two feet because I am a human.}

\textit{Why are they making such a fuss, as if they've witnessed a cow or horse walking on two feet?}

Qing lowered her voice and mimicked a man's voice.

"Stop. Do not approach any further."

Then, gasps, deeper gasps, even stronger gasps than before.

"She spoke!"

"She can talk!"

"She could speak properly!?"

"I thought she was possessed by a ghost!"

It seemed the plague ghost's beast possession was too realistic.

The people of Jianping were disoriented by the plague ghost's sudden human-like appearance.

They were truly simple-minded.

For reference, 'simple-minded' in Zhongyuan certainly does not have a positive connotation.

Among the simple-minded traditions of Zhongyuan was 械鬪\footnote{Mechanized/ organized fight. The term actually first recorded in Qing Dynasty} (Xiedou). What was Xiedou?

It was a time-honored tradition and a display of simplicity in Zhongyuan: invading a neighboring village, killing the men or maiming them to serve as slaves, killing the elderly as useless, and taking the women as spoils of war.

Jianping, a pleasant land with six mountains, one river, three fields, and no interference from government officials, likely had many villages and hamlets in the past.

A discerning intellectual might reasonably infer that Zhang clan unified them, leading to the current flourishing state comparable to a small city.

Of course, Qing was not a discerning intellectual.

Still, it was after she had personally experienced and realized the simplicity of the Jianping people during her beggar life.

If the mind doesn't work, use the body. If your body was good, your head will be at ease.

Anyway, Qing confidently extended her palm forward.

"Stop the violence! I have learned martial arts."

The people of Jianping flinched and stopped their steps.

To the common people of Zhongyuan, martial artists were fundamentally objects of fear.

Martial artists were to be dealt with by martial artists.

Thus, the gaze of the Jianping people naturally turned towards the scarred man, Instructor Kang, the best in Jianping.

At that, Instructor Kang stepped forward.

Instructor Kang's martial arts level was not high.

He merely possessed a dantian, a level considered Second-Rate in Jianghu.

Of course, in such a rural village, even a Second-Rate realm could command respect and fear.

Instructor Kang himself knew his level well, but the reason he stepped forward was because the plague ghost seemed easy to handle.

Just look at the commotion of the past few days.

The plague ghost had only diligently fled and had not physically confronted them.

Why?

She must have been unsure of her ability to handle such a large number of people.

However, at the mention of her having learned martial arts, his mind suddenly became clear.

Why hadn't he thought of that?

Perhaps she had picked up a strange martial art from the Ground Art Fist style somewhere and diligently practiced it.

Of course, even so, it was martial arts practiced for only a few years.

He heard that it had been about five years or less since the plague ghost left, and wouldn't it be remarkable to even barely reach Third-Rate in such a short time?

Nevertheless, Instructor Kang performed a clasped hands greeting.

In Wulin, it was said to be wary of children, the elderly, women, and beggars, so there was no reason not to be wary of the plague ghost, who belonged to two of those categories.

"I am Kang An-ryak, the martial arts instructor of the Zhang Family Estate. Though I am a humble person, I have learned the Iron Blossom Sword."

At that, Qing secretly swallowed a scoff.

\textit{Look at this? He's trying to play mind games?}

Qing was well-versed in the ways of the lower realm martial artists.

It was a kind of large-scale ecological study, comprised of countless cases she experienced during the latter half of her first year, when she was constantly moving around with the 'Evil Punisher.'

\textit{This fellow is pretending to be polite while testing the waters.}

\textit{Well then, I'll have to play along.}

\textit{And there's nothing particularly vengeful about the Zhang Clan Estate, was there?}

Indeed, Mr. Zhang, the patriarch of the Zhang Family Estate, the wealthiest and most influential figure in Jianping, had no reason or occasion to deliberately torment a beggar.

"Plague ghost. No other name was needed. And I have mastered the terrifying, peerless divine skill… yes, the Asura Heavenly Destruction Cat Technique."

"Asura Heavenly Destruction Cat Technique…? Did you say?"

"That's right. The king of beasts, cruel and despicable, a relentless hunter who never loses its prey, swift in movement, traversing the entire world, feared by all—the Beast King! The fur-shedding monster! It is a noble study that seeks to emulate the divine power of the cat."

"No, since when is the cat the king of beasts? Well, it does shed a lot of fur, but-"

"No more questions. Granny Cat\footnote{貓皤皤; Mao Popo} who created this divine skill achieved the position of the world's best with it. Even you, a country bumpkin, must have heard of the Granny Cat's divine power!"

"Ah, no, that's enough…"

Instructor Kang's level of alertness and perceived danger regarding the plague ghost rapidly decreased.

\textit{I think I knew roughly what the situatiom was.}

\textit{The plague ghost who left Jianping must have met some martial arts master.}

\textit{Perhaps that master, for fun or some similar trivial reason, created a martial art based on the image of a cat.}

\textit{And seeing the wandering plague ghost, whether out of pity, or out of curiosity to see if the martial art created for fun had any practical use, or because she wanted to release the martial art she had painstakingly created to the world, she taught it to her.}

\textit{However, that master probably didn't have any particular affection for the plague ghost.}

\textit{Considering that she used an obviously hastily made pseudonym like 'Granny Cat' and left the plague ghost to wander in that beggar-like state after teaching her martial arts.}

\textit{But then, was that a fated encounter or not?}

\textit{If she learned martial arts from a passing master, it would clearly be a fated encounter, but if it was a Ground Art Fist skill like the Asura Heavenly Destruction Cat Technique, then, hmm.}

Just as Instructor Kang, somewhat relaxed, was about to fall into thought over the suddenly appearing astounding topic.

The plague ghost suddenly placed her hands on her waist and spoke with a boastful tone.

"If you understand, then retreat. If you leave now, I will not pursue you."

"How can you be so brazen after causing such havoc in the city?"

"What's the problem with a beggar just begging? Since ancient times, beggars have been traditional robbers who begged by causing trouble."

"Hmm."

It was true that beggars traditionally actively begged, meaning they were the kind of robbers who would invade someone's house, loudly beat sticks, sing, and lie down until they were given food.

It's not wrong.

Instructor Kang sighed deeply and drew the sword at his waist.

"You're completely incorrigible. Words won't work."

"Hoo. You want to have a go at it? Are you truly refusing the 'punishment drink' and opting for the 'encouragement drink'?"

"Punishment drink and encouragement drink are used backwa-, no, never mind. You, no, you brought this upon yourself, so don't blame my methods."

"No more questions! Take this! Asura Heavenly Destruction Dance, First Technique: Fierce Cat Swift Fist!"

At the same time, the plague ghost put both hands on the ground and rushed forward as if skimming the ground.

However, Instructor Kang's expression as he watched the rushing plague ghost was utterly calm.

After all, isn't this an opponent who charges forward, even honestly shouting out the name of their technique?

The threat level of the plague ghost dropped yet another notch, because there were quite a few idiots like this in Wulin.

The name of a technique itself embodies the implications of the martial art and the manifestation of its mental image.

To deliberately reveal that to an enemy?

An experienced enemy would respond like this:

Fierce Cat Swift Fist, if explained, would be something like a fierce cat's swift punch, so ultimately, the true technique would be a punch, a punch as swift as a cat's.

It was difficult to deal with such a low-level enemy, as he had no experience fighting Ground Art Fist.

But ultimately, a punch will come, so focusing on that and counterattacking should easily lead to victory.

The plague ghost rushed forward in a zigzag pattern, leaping along a dizzying trajectory.

Her body movement, mimicking a four-legged beast, was certainly strange and utterly disorienting.

In an instant, the plague ghost, who had surged forward, suddenly dropped low.

Suddenly, Instructor Kang's eyes flashed.

Indeed.

The plague ghost bent her knees sharply, squatted down, and pulled her fist close to her waist.

Instructor Kang's eyes followed the plague ghost's fist, and at the same time, he extended his sword sideways, pulling it in, ready to cut her wrist.

And, thud!

Instructor Kang's waist arched like a bow.

Towards his belly, not his back.

Because the squatting plague ghost had leaped up powerfully and headbutted him firmly in the solar plexus with the top of her head.

"Cough!"

As the breath left his lungs and his chest tightened in excruciating pain, Instructor Kang inwardly screamed.

\textit{You said it was a punch! You said it was a cat's punch!}

If Qing had heard him, she would have scoffed, 'Isn't anyone who falls for that an idiot?'

Qing, who had somehow snatched Instructor Kang's scabbard into her hand, gripped it and swung it down fiercely, shouting.

"Fourth Technique! Fierce Cat Divine Kick! Behold the fierce cat's furious kick!"

At that, Instructor Kang, who had fallen to the ground, grabbed his head and curled into a ball, but still defied her, screaming.

"Aargh! Kick! Aargh, aargh, you said it is a kick! Why, aargh! What kind of kick is this, aargh!"

"It's a kick in my heart!"

"You vile! Aargh, wait, my bones, my bones!"

"That's just how cats are!"

The sounds of Instructor Kang being beaten by the scabbard echoed sharply and satisfyingly.

Then, thwack!

\textit{Oh? What? You caught it?}

Instructor Kang, who had reached out and grabbed the scabbard, let out a rough shout.

"You, you bastards! What are you doing! This bitch, argh, this is nothing, hit her! Hit her!!"

"Whoa! Whoa, whoa, whoa!!"

"Die! Give me back my dongpo pork!"

Only then did the people of Jianping, half a beat too late, rush in!

Instructor Kang had been beaten, but the plague ghost hadn't drawn blood, so it seemed their courage had surged, relying on their numbers.

Qing let go of the scabbard and smiled innocently.

What kind of fighting force could thirty-six ordinary commoners be in front of a Hwagyeong master?

Even if there were a hundred people instead of thirty-six, they would still be in a situation where they had to take a beating.

So, the scene that followed was utterly natural.

"Aargh! Aargh!"

"Gah!"

"Oh, my, ugh."

The men of Jianping were cheerfully beaten.

Punched, elbowed, kicked by toes, stomped by heels, struck by shoulders.

Slapped in the face, clutching their stomachs as nosebleeds gushed, accompanied by wails.

It took only the time to drink a cup of tea for Instructor Kang and the thirty-six men, a total of thirty-seven men, to lie sprawled on the ground.

\textit{It's not even seventeen-to-one, but thirty-seven-to-one!}

One might ask why a woman of Hwagyeong level would boast about that, but anyway.

And a moment later.

The plague ghost clapped her hands together, dusting them off.

Before her were the men, kneeling neatly in six vertical rows.

"Anyway, this town has a lot of characters problems. It's all because of you adults, isn't it? You harass beggars, and then the children watch and learn that, and they think it's okay to harass beggars. Did your parents also teach you that way? Did Jianping, from very long ago, from your ancestors' time, pass down a family motto as a life lesson to harass beggars when you're bored?"

"…"

"…"

"…"

"Answer."

"No!"

"No, ma'am!"

At that, Qing shook her head.

"Don't harass beggars again. Even if you don't help them, you shouldn't kick them, okay?"

"Yes, that's right."

"Understood."

Thus, on a certain day, month, and year.

Northern Liaoning Province.

The plague ghost had pacified the land of Jianping.

As the people of Jianping experienced the plague ghost, she, a master among beggars, the most noble and powerful among them, with great skill.

They feared and respected her, calling her the Grand Supreme\footnote{巨至尊; Ju zhizun}.