\chapter{The Plague Ghost Hides Her Power (1)}

Jianping County, strictly speaking, was not a county.

According to national law, a county refers to an administrative district where the county magistrate, dispatched from the central government, establishes his office and takes charge of managing the entire area.

However, Jianping had no official administrative seat.

It was merely an area where the jurisdictions of Yuangyan County to the south and Pingzhuang County to the west overlap.

This was also the reason why the village was named Jianping: since the two jurisdictions overlapped, they took one character from each place name.

At that time, Yuangyan County was called Jianchang, so the name Jianping was formed by taking the first characters of Jianchang and Pingzhuang.

Usually, it was rare for a city to stand at the very edge of such jurisdictional areas.

Administrative seats were typically established in strategically and economically important locations within a region, so areas spanning the outskirts of two counties usually contained only small villages or hamlets.

However, Jianping was a respectable small city.

This was because its land was incredibly fertile.

In terms of feng shui, it boasts a golden ratio of six mountains, one river, and three fields when considering the entire land, which was considered the best.

Of course, this 'six mountains, one water, three fields' was a concept from the past, when Zhongyuan were fractured and at war.

The mountains surrounding the area were fundamentally rich in resources like trees, herbs, fruits, medicinal ingredients, and animals, and they also make it difficult for enemies to invade.

The importance of water needs no explanation.

Flat land means farming, so it was naturally important.

In this era, mountains were not particularly important, so it all became an old saying.

Anyway, based on the abundant resources from this naturally blessed terrain, Jianping formed the shape of a respectable city.

However, why was this so-called 'honey land', where the population naturally grew enough to form a city, left neglected as a border area between two counties without an administrative seat?

Even though population means taxes?

Because the north was too wide open.

Jianping County was blocked by mountains to the east, west, and south, and bordered the land of the Mongolian barbarians to the north!

Given the nature of the Mongolian horsemen, they wouldn't bother crossing the mountains to invade.

Even if Jianping were raided, that would be the extent of it.

They wouldn't be able to invade further into Zhongyuan territory.

If the barbarians invaded?

They would simply plunder Jianping and then return home on their own, wouldn't they?

Oh, barbarians were living beings, living beings!

They have to eat to live!

However, if an administrative seat were established in Jianping?

Naturally, walls would have to be built for defense, and there would be direct clashes with the barbarians, so troops would have to be stationed.

And if the barbarians were truly determined, they could cross the mountains.

And it's impossible to connect the Great Wall to the mountains.

So, let's just leave it as is.

It's outrageous that the people of Jianping evaded taxes, but it's far more economical to not establish an administrative seat and just let them live on their own.

This was precisely the cold principle of governance!

In fact, the people of Jianping were periodically plundered by Mongolian barbarians.

When Mongolian cavalry entered the city with carts, the people of Jianping would rise up indignantly like righteous volunteers and rush at those lawless barbarian savages, holding bags of grain.

From the barbarians' perspective, there was no reason to violently disturb the people of Jianping who quietly supplied food.

On the contrary, if they provoked them unnecessarily, they might bring in government troops, or the common people might move away, so they would take what they needed and withdraw.

It was a very peaceful scene of plunder.

Then, one might ask, isn't it just offering tribute to the barbarians rather than plunder?

'Shush! Oh dear, what a dangerous thing to say.'

'It's plunder, plunder, always plunder.'

'Do you think we made offerings because we liked it?'

And so now.

The courage of the Mongolian barbarians who once ruled the world was forgotten.

The government and military have buried it out of interest.

And no one points out these things.

Now that plunder has become a rigged deal,

A beggar was walking on a mountain path.

The beggar's appearance was exceedingly strange.

First of all, she was a beggar.

Her attire, for starters, looked like a beggar's.

It was a very beggar-like state.

In fact, if her attire had been decent, she would have been called a woman, not a beggar.

The very implication of the word 'beggar' includes wearing beggar-like clothes!

What was particularly strange was her hair.

Her long hair was disheveled, covering her face, a grotesque sight that would be terrifying to dream of, like a ghost.

One couldn't tell when she last washed her hair; the greasy, shiny hair was tangled together, showing no movement even in the biting winter wind.

What on earth was the true identity of this strange beggar, this very beggar-like beggar!

The identity of this beggar-like beggar?

None other than the new star of the orthodox Wulin, a once-in-a-generation prodigy who achieved the youngest Hwagyeong realm!

Known as Heavenly Blossom Zword, the most influential star of Zhongyuan that all women under heaven wished to emulate!

The sole female and shining intellectual of the Hanlin Academy!

Sometimes, she was also a medical woman who saved lives.

And sometimes, she was a carpenter-shaman, building homes for people, and homes raising people.

And at other times, the greatest mystery of Wulin, the Divine Thief, the Greatest Thief Under Heaven, a total bandit!

Sometimes, she was the pinnacle of Zhongyuan mechanical formations, and at other times, a gourmet maniacally craving meat.

Thus, her ever-changing true identity, whose nature could not be guessed, was-

Heavenly Blossom Sword Ximen Qing, Ximen Tianhua!

And today, Qing had returned to her origin and foundation, her primordial mindset.

Today's Qing was the plague-stricken beggar of Jianping, the plague ghost herself.

Of course, if one were to observe the current plague ghost up close, several suspicious circumstances might be apparent.

Although she wore several layers of dirty rags stained with grime, the absence of any foul odor indicated that the stains were merely ingrained dirt, and the clothes were actually cleanly washed.

If one were to bury their nose in her greasy, matted hair, the faint aroma would reveal that oil had been deliberately applied.

But who would pay such close attention to a mere beggar?

Especially when her face was covered, and through her limp, matted hair, one could glimpse the festering skin of a sick person, rising with blisters.

Qing looked down at the wide basin from a tree on the mountainside.

The landscape of the city, standing tall amidst a vast snowfield where a considerable amount of snow had fallen, with cultivated fields spreading widely around it.

It was truly a snow country, a truly beautiful and modest landscape.

Of course, she wasn't so enchanted by the snow that she forgot the ugly hearts of the people in that ugly city.

\textit{But, now that I'm back.}

\textit{How can I make it known that I've returned successfully?}

\textit{Should I go to Jianping Pavilion and cause a ruckus?}

\textit{You sons of bitches, enemies of food waste, the grudge of stolen leftovers, I will never forgive you?!}

\textit{Or should I behead the beggar king's head and hang it in the middle of the market?}

\textit{Hmm, I'm somehow less inclined to do that.}

\textit{Even if I make a grand entrance, that's all it would be.}

\textit{If the disappeared beggar returns as a super-strong beggar who has mastered martial arts, wouldn't everyone just bow their heads and apologize then?}

\textit{Of course, watching that spectacle would be fun.}

\textit{No, no.}

\textit{Now, I will conceal my strength.}

It was also a test Qing was setting.

Her intention was to quietly enter and see if the public sentiment was still as bad, and how the plague ghost would be treated.

\textit{If the people of Jianping, having lost the plague ghost, then regretted their harshness and became new people?}

\textit{Then, I would have no choice but to treat them courteously.}

Anyone can make mistakes, but isn't it precisely because they can correct them that they were human?

…What nonsense!

Crash! A snowball hit Qing's head and shattered.

Of course, to break Qing's head, a mere snowball wouldn't even come close.

Qing's body had already transcended human limits, the hardness of her head also transcended human limits, so throwing a mere lump of snow couldn't even cause the slightest damage.

Then, thwack!

A clear vein popped on Qing's forehead.

\textit{Shit, which bastard put a rock in the snowball.}

Of course, a rock was also too fragile a material to break Qing's head.

It might caused a scratch on the skin, but a rock without Inner Qi was far from enough to even tear the skin.

\textit{But it feels disgusting.}

\textit{These bastards really haven't changed at all.}

In fact, it's late February now.

Late February means people were quite bored.

Of course, people in this primitive era with no entertainment were always bored and thirsty for fun.

Especially in winter, they have nothing to do and were writhing in boredom.

Amidst this, exciting news struck Jianping.

"Did you hear? They say the plague ghost is back!"

"Plague ghost? Who's that? The ghost-like woman with only a decent chest from before? Wasn't she dead?"

Who was the plague ghost?

She was that beggar who appeared sometime five years ago, or even longer, was seen for about half a year, and then suddenly disappeared without a trace.

Of course, one might ask if there was only one or two beggars who appeared in the city and then vanished without a trace.

But the plague ghost was unique.

First of all, her appearance was horrible, with blisters all over her face and marks from burst and festering sores, a sight one couldn't bear to look at.

Yet, her body was perversely enticing, and she hid her face by letting her hair down, so she was quite a sight to behold, a beggar who offered considerable visual entertainment, one might say.

Especially when one threw stones or showed her a stick, she would get scared and run away, and at such times, her shaking flesh was quite a spectacle.

Of course, no matter how enticing her body might have been, there was no idiot in the world who would want to sleep with a beggar afflicted with a strange disease.

"Beggars have lives as tough as steel wires, you know. She must have gone somewhere else and been chased away."

"Where is she? I'm bored, this is perfect. Let's go right now."

The man jumped up from his seat.

Usually, tormenting beggars was uncommon.

A person with nothing to lose was more feared than a person with something to lose.

Bluntly speaking, a beggar, if things went wrong, could just stab someone or bludgeon them with a rock, kill them, and then escape.

But there was an exception to this.

Sick beggars, disabled beggars, and child beggars were exceptions.

How harsh the world was to weak beggars whom one could torment without fearing repercussions.

This was not because Zhongyuan people were evil.

Humans seek to restore their self-esteem by tormenting those weaker than themselves, and thereby revel in the base pleasure of feeling superior.

By nature, every human was a beast harboring such wicked desires.

The act of power abuse was precisely the outburst of such base desires.

These past few days.

Jianping, which she infiltrated, had changed greatly, and at the same time, had not changed at all.

The big change was the disappearance of beggars.

\textit{Why are there no beggars in the city?}

\textit{Where did all these bastards go?}

They weren't completely gone, but the beggars she saw were somehow unfamiliar, and the only emotion in their eyes was the wariness of seeing a new competitor in the same industry.

To Qing's eyes, they were also unfamiliar faces.

The original beggars were nowhere to be seen, nor were the beggar gangs that usually existed in every city.

The comfortable underpasses, ruins, and caves where the beggar kings used to live were also empty.

It was a good spot for a beggar, so an unfamiliar beggar was occupying it, but wasn't she a new (?) beggar Qing didn't know?

\textit{What?}

\textit{Where did all those beggars go?}

The answer is, they were all rounded up and were now doing forced labor as government slaves in the mines north of Shanxi Province.

Qing didn't know, but the beggars who were originally in Jianping had unknowingly incurred the wrath of a very, very important person and were sentenced to lifelong hard labor.\footnote{Lesson from this story: Don't mess with the Empress' daughter}

This was truly a lenient measure.

Originally, instead of New Year's fireworks, there was going to be a New Year's artillery festival.

But what then?

If Jianping disappeared, the barbarians would starve.

If the barbarians starved, they would come plundering even over the mountains.

Plundering happened somewhere every day anyway, so it didn't matter much, but what if, in the process, the Mongolian barbarians opened up mountain paths?

That could become a big problem then.

Through this thought process, the ministers desperately rose up, and Jianping survived.

Of course, it was also thanks to the fact that when the Western Palace officials who visited for investigation collected evidence, the testimonies of Jianping's common people minimized the part about tormenting the plague ghost.

After all, who would brag about tormenting beggars to outsiders?

Of course, Qing didn't know any of this.

The people of Jianping regarded the plague ghost as a human-shaped beast whose words couldn't be understood, so there was no way for her to overhear anything.

\textit{These Jianping bastards finally caught the beggars.}

\textit{Or did those scoundrels from Jianping Pavilion finally put poison in the leftovers?}

\textit{Well, anyway. It's none of my business.}

On the other hand.

What hadn't changed was Jianping's average personality.

Throwing snowballs was considered a minor prank.

Qing took note of the bastard who threw a rock.

\textit{But wasn't the bastard who sprayed water going too far?}

Spraying water on a person in this cold.

Let's say the guy who brought a water pouch and squeezed it out to spray her was just playing a prank.

But the bastard who scooped up a basin full of water and cautiously approached, because it was heavy—is this even a human being?

The basin guy suddenly tripped and ended up drenching himself with all the water.

He must have fallen badly, because his ankle broke with a loud crack, making him a truly pitiable sight.

Anyway.

Besides that, they threw inedible things.

\textit{Well, I did used to specialize in showing off my 'eat anything' skill.}

Among the worst was Kushu\footnote{\textit{Picrasma quassioides}; bitterwood}.

Kushu was so incredibly bitter that no matter one's constitution, putting it in one's mouth would involuntarily cause one to gag and vomit.

And why would they go to the mountains to peel the bark of this useless Kushu tree, which has no practical use, just to throw it at her?

They wanted to see her gagging and going crazy while eating, that's what.

Besides that, kids poking her with sharp branches, well.

When adults were acting like this, wouldn't kids naturally watch and learn?

\textit{Hmm. They're all utterly despicable bastards.}

\textit{Is this Jianping's average?}

\textit{Truly, I couldn't be more grateful.}

\textit{Thanks to them, I won't feel sorry no matter what I do to these guys.}

"Kukuku kuhukuk…"

The plague ghost was laughing.

It was a very ominous laugh.

However, the people of Jianping did not know what the plague ghost thought.

"What? Brother. This bitch is laughing?"

"Leave her alone, she must have lost her mind."

And they just scoffed.

What would their future hold?