\chapter{The Plague Ghost Hides Her Power (4)}

Peaceful Jianping was no more.

A storm was brewing in Jianping.

"There! Get her!"

"Why is that beggar woman so nimble!?"

"Well, she's running on all fours, so she has to be faster than on two!"

"What, what!? Are you a genius?"

The residents of Jianping, wielding clubs, shouted, 'Catch that bastard! No, that bitch!' as they rushed forward, shoulder to shoulder.

On the opposite side, the plague ghost, now truly a dangerous beast, was racing away on all fours, bounding swiftly through the streets.

"Herd her! To the right, to the right!"

"Right! Quickly!"

Qing's eyebrow twitched slightly as she ran.

\textit{What? Herd me to the right?}

\textit{I can hear everything, you know? I have ears, you know? I can understand.}

Of course, this current form of hers—the plague ghost who entered Wulin learning a bizarre martial art that turned her into a beast—was set up to literally become like a beast.

Even so.

"Waaaaah! Waaaaaaah!!"

"Kiiyooooh!! Kiiyoooooh!"

\textit{Why are they shouting?}

\textit{Are they really herding a wild animal?}

\textit{Do they think I'm a real animal?}

\textit{At this point, I'm a little curious.}

\textit{What did they prepare on the right side?}

\textit{Hmm, I can't ignore their sincerity.}

Anyway, the difference in weight class between Qing and the people of Jianping was very clear.

If Qing was a tiger in her prime, the people of Jianping would be like three-year-old toddlers just learning to walk, a suitable analogy.

In fact, even if Qing just lay down and took a beating, adding her transcendent body and Protective Qi to her already superhuman physique, she could simply be beaten until the people of Jianping tired themselves out and collapsed.

Just as a three-year-old child genuinely hitting a tiger would cause no damage.

Qing feigned being driven, slipping into the right alley and sprinting.

And what she saw on the other side was—

What was it?

A serving dish neatly placed on the ground.

On the dish was a roasted duck.

And on the walls to the left and right, men holding nets, holding their breath in anticipation.

\textit{What on earth is this?}

\textit{They're really hunting a wild animal, aren't they?}

Qing let out a quiet sigh.

\textit{Ah, truly, I am such a person.}

\textit{Not only am I the youngest Hwagyeong, a transcended Hwagyeong, a proud medical practitioner, and an expert in construction, but now, as a perfect beast, is my acting even the strongest?}

\textit{Because I'm so outstanding, I have to see all this.}

In fact, Qing's actions right now were just play.

She was just playing around.

If someone who knew Qing saw this, they would let out a long sigh, thinking, 'This bitch, she sent her friends away and came alone just to do this.'

And that was the truth.

Someone like Jian Buxi, who was supposed to come with her, would just calmly, foolishly, lewdly, yet benevolently affirm whatever Qing did, even if she acted like a dog.

Jian Buxi was family, wouldn't she warmly embrace Qing even if Qing became a real dog, not just acted like one? 'Wow, Xiao-mei has become a dog.'

However, this was certainly not a sight to show to other acquaintances.

Knowing that, yet still stubbornly putting on this outrageous display, could be said to be utterly incorrigible.

Anyway, Qing met their expectations.

She eagerly rushed to the dish, grabbed it with both hands, and took a large, wild bite.

"Now!"

"Now!"

The men's shouts, 'This was the moment!'

Qing feigned a startled jump, raised her head sharply, and then sprinted away on all fours again.

A large net landed precariously behind Qing, of course, this was also Qing's performance, as she could sense her surroundings completely due to her Awakened Sense Divine Art.

"Aargh!"

"You should have thrown it faster!"

"Damn it!"

The regretful screams of the Jianping people echoed.

But that was only for a moment.

Among them, a man with a scarred face, from his left eye down his cheek to his jaw, sternly gave orders.

"I knew this would happen, so I had them put poison in the dish! She'll soon vomit and collapse. Chase her!"

"Ah! As expected of Instructor Kang!"

"Truly the best in Jianping!"

The men regained their strength and ran again.

Since she ate poison, she wouldn't be able to go far.

"Chase her! Huff, huff, chase, chase!"

"Don't, huff, huff, huff, hit, argh!"

She wouldn't be able to go far…

But the poison has been replaced by spicy flavor.

"Huff, huff, huff, huff, huff, huff."

"Can't, huff, anymore, argh."

"Ugh, ueeek…!"

The people of Jianping collapsed one after another, and due to excessive running, stomach acid spewed out everywhere.

The plague ghost, having earned a point, gracefully and lightly moved away as if showing off.

Plague Ghost Extermination Operation, Day One.

Failure.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Jianping was a basin surrounded by mountains; more accurately, the mountains encircled it like a liquor bottle, with a narrow opening to the north.

If you follow the narrow opening to the north, you'll find a wide plain, and as you go further north, the land becomes worse, vegetation decreases, and the height of the grass lowers.

That was the land of the Mongolian barbarians.

And the Mongolian barbarians call this place by this name:

Zaruuk Plain.

Somewhere on the Zaruuk Plain, about thirty round tents were gathered.

These were the yurts, the tent-houses of the Mongolian barbarians.

And in the center, there was one enormous yurt that dwarfed all the others.

Generally, in all civilizations, the size of a house indicates the status of its owner, so this enormous yurt was the privilege and symbol of a great warrior who commanded a tribe.

And the great yurt on the Zaruuk Plain belonged to Nainforukdeok, the great warrior of the Patuk tribe.

And in front of that yurt, a young warrior shouted loudly with a mighty voice.

"Great Warrior! The Khan's envoy has arrived!"

Khan was originally a title for the ruler of all Mongolian clans, meaning the Mongolian Emperor.

However, to commemorate the great Mongol Empire of the past, the largest empire in human history, and once the strongest conqueror who conquered the entire world except for the New World, he was called the Khan of Khans, the Genghis Khan.

After that, Khan was demoted to the ruler of a great tribe.

After the empire was torn apart, the Mongolian barbarians also split into tribal units, and it has been over four hundred years of history since they fought among themselves in tribal struggles.

So, even a Khan was just one of countless Khans, not necessarily an incredibly powerful figure.

No matter how great a Khan, he cannot treat a great warrior who leads a tribe with disrespect; what if the warrior goes to another Khan?

So, if a Khan treated a great warrior with respect, that was common, but it was now rare for a great warrior to treat a Khan as a superior… but.

Nainforukdeok lay flat on his stomach in front of the hearth in the center of the yurt!

This was a posture of extreme reverence.

"I greet the Khan's envoy!"

At that, the Khan's envoy, as if it were natural, settled himself on the master's seat directly opposite the entrance.

It was a highly disrespectful act according to Mongolian barbarian custom, but Nainforukdeok paid it no mind, rose from his seat, and took a seat on the left.

And then, silence.

For about half \textit{ke}, neither spoke, so it was naturally just quiet.

Then, the Khan's envoy opened his mouth.

"The Khan commands. Prepare to slaughter the sheep and hunt the hens!"

At that, Nainforukdeok's expression brightened considerably.

"Ah, finally!"

And then, silence again.

It was around the time another half \textit{ke} of silence had passed.

The Khan's envoy abruptly stood up.

He walked out with decisive steps and then, 'Hya!' the sound of a Mongolian barbarian urging his horse.

The rapidly fading sound of hooves, clatter-clatter-clatter.

And that was the end of it.

If Qing had seen this, she would not have been able to hide her bewilderment, wondering, 'What on earth is going on?'

In fact, any Zhongyuan person, not just Qing, would have felt the same.

To specifically come, receive a bow.

Sit down and act important for a long time.

Prepare to kill sheep and catch hens.

Utter one terse sentence.

And then, again, act strict, solemn, and serious, only to suddenly go home, wasn't that the situation?

But this was what the Mongolian barbarians called the conversation of men.

It was the manly demeanor that serious men should uphold!

That's right.

The path of a true man was this difficult, and thus, it was said to be worth challenging.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Plague Ghost Extermination Operation, Day Two.

Failure.

Plague Ghost Extermination Operation, Day Three.

Failure.

Qing was disappointed.

The fact that there were no decent martial artists in Jianping was something she had known for a long time.

Wasn't one of the reasons she lived as a beggar for a whole year precisely because of this environment devoid of martial artists?

If Qing had seen the amazing sight of martial artists early on, with light coming out of swords, coolly swinging something like a lightsaber, and people flying around—

She might have abandoned her beggar life long ago and rushed out of Jianping to learn martial arts.

However, Jianping was actually closer to the medieval Zhongyuan of her homeland.

This was also why Qing remained in a state of 'don't know anything about Wulin' even in her second year in Wulin.

\textit{Still, half a decade had passed, I wondered if anything had changed, but besides the guy with the big sword scar on his face, everything was the same, wasn't it?}

\textit{Even the guy with the sword scar is only at the second-rate level.}

\textit{Is this Jianping's average…?}

Literally, it was so boring she wanted to die.

One might retort, considering that, weren't she playing quite earnestly?

\textit{But, well, I just feel like doing this.}

\textit{How long have I been oppressed? Isn't this much torment rather a lenient measure?}

Qing didn't know, but the more trivial Jianping was, the more a certain lump in her heart was melting away.

Because for a nightmare of the past, engraved and unforgettable, realizing that it was truly nothing at all could be the solution.

Plague Ghost Extermination Operation, Day Four.

Failure.

Qing's movements gradually became simpler.

Muscles she didn't usually use were quickly trained, and she became accustomed to movements she didn't usually perform.

This shameful spectacle of running on all fours without using Inner Qi was gradually becoming ingrained in her body!

Lower-level martial artists might ask what meaning there was in becoming accustomed to such a pathetic posture, which one couldn't bear to look at.

But masters see it differently.

Becoming accustomed to such movements means that one can perfectly control one's body even while performing these bizarre movements.

This was a move that an enemy cannot predict or counter.

And in Wulin, such a move was called by another name:

Life-Saving Ultimate Technique (救命絶招)!

Even if not for that, martial arts were not originally created to fight enemies much shorter in stature.

The practical effectiveness of these four-legged movements has actually been recognized since ancient times.

It's just that they were too ugly and undignified to use.

Even masters of Ground Art Fist\footnote{地术拳; De Shu Quan}.

The type of martial arts performed by running on all fours, crawling, or staying low to the ground was called Ground Fist Arts.

Masters of Ground Fist Arts even went so far as to make this claim:

'Because Ground Fist Arts was so threatening and deadly, and there was no way to stop it, Zhongyuan Wulin prevented everyone from using with the excuse of dignity!'

Of course, this was the claim of those who use Ground Art Fist.

It's like the context where people who practice Fist Arts\footnote{拳法; Quan Fa} make claims that won't be taken seriously, such as 'strong even without weapons,' 'human's inherent potential,' 'it's not that we don't have money to buy weapons,' and so on.

However.

The scarred man, known as Instructor Kang, the best in Jianping, was not a master.

So, even seeing Qing's actions, he would just grit his teeth, thinking that the beggar woman was as nimble as a beast, or even more nimble than a beast.

Naturally, he had no choice but to grit his teeth.

He had a martial artist's pride, how many days had he wasted trying to catch a single insane beggar woman?

However, behind Instructor Kang was Elder Jang.

And in this remote area without an official administrative seat, the authority of a local influential figure was truly beyond imagination.

Plague Ghost Extermination Operation, Day Five.

Qing was dumbfounded.

\textit{What is this? They're going this far?}

She was getting a little tired… no, she was still feeling invigorated and having fun. Then she entered an alley?

It wasn't a narrow alley.

On this path, wide enough for ten adults to walk arm-in-arm, they had built a tall barrier!

Of course, the barrier was hastily constructed and not meticulously done, but Qing had never seen such a barrier being built.

If Qing hadn't seen it, it must have been when she was asleep.

These days, she was sleeping very soundly—since she stole food after sunrise, played hide-and-seek, stole food again, and ran around all day without using Inner Qi, it was inevitable that she would sleep soundly—even if it was almost like passing out when she slept.

\textit{So, they built all this in one night?}

\textit{Just to catch me?}

Even Qing couldn't help but admire their passion.

Of course, could it be done with passion alone?

It was a miracle that happened overnight, a historical event brought about by the influence of Elder Jang, the master of Jianping.

While Qing was admiring it, a rough, mocking laugh came from behind her.

"Heh heh, you finally got caught, you bitch."

At last, finally, now!

The people of Jianping filled the wide alley, approaching step by step.

At that, Qing thought, \textit{Hmm}.

\textit{It seems hide-and-seek ends here.}

\textit{Still, if they built a wall in the alley overnight, wouldn't it be polite to let them catch me, even just out of respect for their effort?}

So, hide-and-seek ends here!

But?

An eye for an eye, a tooth for a tooth.

Triviality for triviality.

For a whole year, she couldn't remember having a single comfortable meal.

And the resentment from those sorrowful meals had been repaid in the same way, this settled it.

On the other hand, during her beggar days, she never traveled with peace of mind, always hiding and running, always struggling.

And that resentment was repaid with an extreme, endless game of hide-and-seek, causing many to vomit.

\textit{But, I did get quite beaten during those unfortunate beggar days, didn't I?}

\textit{Then?}

\textit{It iss time to repay that grudge.}