\chapter{The Plague Ghost Hides Her Power (10)}

The Mongolian barbarians underestimated Qing.

It was an unavoidable fate of their people.

Zhongyuan puople had long learned through bitter experience the so-called 'Hidden Killers' of Jianghu, which states that one must be wary of one of the following: children, elderly, women, the disabled, the sick, beggars, and monks.

Thus to the people of Zhongyuan, the current combination of Qing, a sickly woman beggar, and the addition of would-be beggar child, was nothing less than the symbol of a hidden powerhouse.

But the Mongolian barbarians followed the solemn teachings of their Great Khan.

'Kill anyone taller than a cartwheel!'

By this logic, everyone except children and women (spoils of war) should be slaughtered, because children and women were easy prey!

This was the precious wisdom of Genghis Khan, the ruler who came closest to unifying the world, and whose empire spanned the largest territory in human history.

It stood in stark contrast to the ancient proverbs of Zhongyuan' Wulin. which only made Qing seem all the more insignificant.

They even considered her head a worthy trophy to decorate their ger\footnote{Mongolian term for yurt}, thinking it might hold some value as the 'ugliest head in the world'.

Two Mongolian warriors spurred their horses forward.

Hiiiiing! The well-trained warhorses charged toward Qing with a fierce cry.

Beside Qing, Murong Jun's youthful voice rang out.

"Come on!"

"Warrior Lu!"

"Wait, me too—!"

Warrior Lu scooped up Murong Jun and leaped away in a single bound.

Qing stood alone calmly watching the charging cavalry.

\textit{Hmm. I had left Moonlight Sword behind and is empty-handed, but now weapons are conveniently rushing toward me?}

One wielded a ge\footnote{戈; a polearm with a hooked blade} and the other a zhanmadao. The latter suited Qing's taste better.

In an instant the distance closed. The fearless horse lowered its head to ram into Qing.

Horses were naturally very timid creatures, but well-trained warhorses were vicious beasts that could trample and bite.

\textit{A mere beast daring to charge at a master of the Hwajing realm? I could have its skull shattered in an instant.}

But Qing simply took a step to the left leaning her body slightly to avoid the horse's head.

"Al-wala-il-la-il-la-il-la-il-la-aaa ...

The unique, long, drawn-out, and raspy screams of the Mongolian barbarians ring in her ears.

\textit{No, what kind of battlecry is this?}

The horse's head passed Qing, and the rider on it barely grazed Qing's chest.

And the blade followed.

A weapon with a long blade hook attached at a right angle below the blade.

As the horse ran with its hooves hanging behind it, the sword hooks of the hooves following it rushed forward, aiming for the Qing's neck.

Qing bent her knees.

Her body lied horizontally, with her back almost touching the ground.

At that moment, a shining blade brushed past.

Where the neck was, it passed through the air, leaving a long, thick trail behind.

Qing's eyes suddenly open wide.

\textit{What was that? Sword Qi? No, Sword Force? Since it's ge, so it's Ge Qi?}

\textit{No, what kind of barbarian uses martial arts in the first place?}

\textit{Aren't they just wandering savages on horseback?}

Just as the Mongolian barbarians looked down on the Qing, Qing also looked down on the barbarians!

\textit{But, so what?}

\textit{Judging by the aura of the weapon's Qi, it's somewhere between the First-Rate and Early-Peak, so isn't it no different from Third-Rate?}

Just before Qing completely fell, the back of her hand hit the ground roughly.

She recoiled up with her knees bent, and ended up in a Horse Stance, glued to the ground.

"Ulzzang!!"

The second horseman, carrying the zhanmadao adorned with a bright porcelain hilt, suddenly lifted his weapon.

At that moment, Qing's knees spread and his body was shot out diagonally.

The palms that had been curled up next to her waist rose up, passing by her ears and above her head, and a vicious Qi flowed from Qing's dantian through her Qi meridian and towards her long arm.

Qing's palm sank against the barbarian's chin, and long, graceful fingers grip his lower jaw tightly.

Clutching the barbarian's face with one hand, Qing shot up straight.

The barbarian's zhanmadao floundered.

Within a moment, the person being held by one person soared a full foot and a half, reaching a peak approximately the height of the roof of a two-story building.

It was said everything that falls has wings.

Because you have to fly up before you fall.

Qing's right arm drew a large arc.

The lower body of the barbarian captured there also drew a curved line, with the torso rising toward the sky and the head turned over toward the ground.

Qing's hand were blackened with charcoal, and the skin beneath the charcoal had a jet-black sheen.

One of the Ten Great Demonic Arts Under Heaven! Black Slaying Demonic Palm!

Qing thrusted her lower arm into the ground with all her might.

Boom! With a loud noise, a crater opened in the ground, a circular crack forming.

"Huuu."

In the center of the pit, Qing slowly stood up, after landing in a cool pose on one knee.

At her feet, the torso of the barbarian was twitching under a completely compressed helmet.

Qing tap her knees and, while bending down, casually snatched the zhanmadao from the corpse's hand.

\textit{Ah, this heavy, cool feeling.}

\textit{The blade itself is shorter than the Moonlight Sword, but it is a wide and heavy sword, so it should have a satisfying feel when cutting with it.}

Qing straightened her back and looked around at the barbarians who were still in shock with an arrogant look in her eyes.

And then just one word.

"Next."

"[Odoksain!! How dare you, you bitch!!!]"

One of the barbarians shouted and rushed out on his horse.

But Qing was calm.

She even had time to think about other things.

\textit{So the name of this friend who just gave me zhanmadao is Odeoksa, or as I heard, Ojusurang, which is a strange name.}

\textit{How come the person's name is Oh Ju-su-raeng? It seems like a name that would be good for controlling fever.}

Qing was very relaxed.

Because she had already seen through their weaknesses.

The reason why there were no kicks Divine Arts in martial arts was because the advantage gained by stepping on the ground was greater than striking the enemy by swinging your feet.

The feet of a martial artist were the starting point of movement of the body and the center of all attacks, so martial arts were skills that unfold from the feet.

But what if you ride a horse?

Even if you were in a relationship where you communicate with each other, where you become the horse and the horse becomes you, can we expect movements as delicate as a human foot?

This time, Qing took a step to the right and jumped up, sending the zhanmadao flying.

The outstretched left hand struck the barbarian's lower body!

Back to the sky. Her left hand drew a line.

Thud! A cobweb-like crack etched into the ground, a pit dug, and another corpse, blood spurting from its neck beneath a crushed head, was added.

The left and right were reversed, but the exact same method was used to finish off a barbarian.

Then, with her left hand, she took the winner's rightful right, the spoils of war, and stood with a huge sword on each side.

And then, Qing immediately regretted it.

\textit{Oh, right. I should have hidden my power more.}

\textit{Once might be a coincidence or luck, but twice it becomes a skill.}

"[You despicable bitch, hiding your true colors! Warriors, that bitch is a master! Fight in formation! You can't attack her head-on!]"

A battle of cavalry. And the sight of barbarians hastily hanging their weapons on their saddles and drawing their bows.

Then Qing took a deep breath.

The already huge chest swelled to the point where it threatened to burst the clothes she was wearing, and soon a huge voice sweeps through the room.

"[Hold on!!!]"

The barbarians stopped at that.

Qing then speaks in a solemn voice.

"[I've eaten buuz before.]"

Apart from her fluent Mongolian language, her voice was so mournful that it didn't match the content at all.

"[What?]"

"[Buuz, the baozi\footnote{dumplings} you Mongolian barbarians eat. They're filled with lamb, and the filling is made with lamb fat, boiled in a rich broth. It's truly exquisite. Apparently, the thick dumpling skin is used because of the rich fat content, but the two go together to create a truly heavenly flavor. Hmm, now that I mention it, I really want to eat buuz.]"

"[What nonsense are you talking about-]"

"[However!]"

Qing spread both arms wide.

"[Is buuz really the food of you Mongolian barbarians? The name buuz itself came from baozi, a wonderful cultural heritage of Zhongyuan. So aren't you stealing the food of Zhongyuan and daring to claim it as your own?]"

The veins on the foreheads of the Mongolian barbarians were crackling.

The Buuz Plagiarism Theory came out of nowhere, but somehow it also scratched people's nerves.

The Mongolian barbarians should have covered their ears.

Even the Grand Elder of Tang Family acknowledged the formless poison, and the moment you listen closely, you were already addicted. How could you handle this vicious poison?

One hot-tempered barbarian finally managed to vent his anger.

"[If you're going to be so picky, what about the noodles first created by our great steppe children? You Zhongyuan people make all sorts of noodles and claim them as yours, but all the noodles in the world actually originated from our steppe—]"

"Gal!!!! [That's not important right now! I have something more important to talk about! And that's Khorkhog!]"

"[Why khorkhog, khorkhog is our meadow-]"

"[That's right! I was so moved that I shed tears when I ate khorkhog before! Its appearance, refusing any vegetables or even a single scrap of grass, with only meat, was the boldness of the men of the plains, and the cooking method of cooking it with a hot stone was truly unique, unparalleled anywhere in the world!]"

Then, above the heads of the Mongolian barbarians, a question mark in the style of Qing's homeland, appeared.

'Why the sudden khorkhog praise?'

Either way, Qing spoke passionately.

"Khorkhog is truly delicious! Even those who have lost their sense of taste will regain it after one bite. This is what it means to be delicious! A powerful roar ripples down your tongue, a violent taste! It is truly the most delicious dish between heaven and earth!"

The expressions of the Mongolian barbarians were sour.

\textit{Khorkhog is tasty, but is it that good?}

Qing scolded him again.

"[You should have eaten Huhheuk! You should have eaten Huhheuk!!!]"

At the same time, bang! The sound of feet stomping!

Qing's figure stretched out, drawing an afterimage.

Bang! Bang! Bang! Heavenly Demon Reigning Steps, reaching maximum speed in three steps, rushed through the cavalry in an instant.

Nainpo-reuk-deok, who had just raised his bow and drawn the string, felt his heart pounding at the sight of an afterimage of a demon behind the crazy woman.

\textit{You bitch! You've been raving about nonsense, and now you're rushing into the midst of the warriors, preventing them from shooting their arrows!}

\textit{A bitch who knows how to fight, no, a bitch who knows how to wage a battle! This bitch is dangerous!}

"[Damn it! Scatter! Scatter! Disengage formation! Don't cross the firing lines!]"

If Qing knelt, it was to induce the enemy to let down their guard. If she spouted nonsense, it was also to induce the enemy to let down their guard.

Qing's combat intelligence was the fighting brain that grew exponentially in the face of slaughter.

"Let's go!!"

The two zhanmadaos spun fiercely.

The fundamental principle of a heavy, gigantic weapon was to draw a circle by rotating the body, and since she was carrying not one but two, it would be difficult to control with human strength otherwise.

Of course, Qing's strength had already surpassed human level, but there was no reason to give up a better method just because it was possible.

The already enormous zhanmadaos let out a whoosh sound! The monstrous blades soared, with tremendous amount of Qi shot out in all directions.

The handle was two and a half \textit{zhang} long, with the blade added it was three \textit{zhang} long, and there were not one but two vicious blades that were one and a half \textit{chi} wide.

A whirlwind of blades spinning at a terrifying speed engulfs the retreating horse.

Chunks of meat flew in all directions.

Some had horse skin attached to them, some had human fingers, and some had pieces of intestines.

Thud thud! The sound of slightly undercooked meat falling like rain.

It was the moment when a horsed archer disappeared without a trace.
