\chapter{The Plague Ghost Hides Her Power (9)}

Qing had expected the Mongolian barbarians to look like savages, with pots on their heads and ridiculously bushy beards

Surprisingly, they were quite clean and human-like.

\textit{Hmm just people on horses…}

\textit{Quite disappointing, really.}

\textit{Especially with those furry winter hats or helmets?}

\textit{Wait, wasn't it said that the small inconvenient grills used for lamb back home were inspired by Mongolian helmets?}

Of course that wasn't true.

That kind of lamb barbecue wasn't even Mongolian cuisine to begin with, but a dish created by Dongyi barbarians.\footnote{Jingisukan (ジンギスカン), or  'Genghis Khan' is Japanese grilled mutton dish. It's a modern invention, created between 1920-1930.}

Leaving aside the origin of the dish, what kind of army would use their precious helmets as makeshift grills?

That would ruin the metal and make it useless for protecting their heads, not to mention the strong smell of meat every time they wore it.

While Qing was having a slight sense of disappointment, the thirty or so horsemen clattered closer.

It was a martial artist's habit to instinctively assess their opponents' gear.

Three of them carried long spears with flags, while the rest were evenly armed with halberds, guandaos and zhanmadaos.

Halberd refer to a spear with a hook, guandao refers to a polearm with a crescent moon blade, and zhanmado refers to a long sword with an extended handle. So, it were all weapons that are good for swinging from horseback.

Additionally, each had one or two bows strapped to their waists, fitting the infamous Mongolian fighting style of shooting arrows from horseback like cowards.

Anyway Mongols. Mongolian barbarians.

After displaying their impressive horsemanship by splitting into two lines, one rider slowly emerged from the center.

He was clad in a shining golden silk robe, and the black horse he rode was tall and sleek, and had a neat sheen to its jet-black hide, making it a true fine horse among fine horses.

He was clearly the leader.

Naturally all eyes were drawn to him.

\textit{Probably rehearsed, right?}

\textit{The image of Mongolian barbarians practicing such an entrance in an empty field, well, is a bit ridiculous.}

\textit{But then again, armies are strict about protocols.}

The people of Gyeongpyeong knelt and bowed their heads.

The leader spoke with a satisfied smile on his face.

"Yes, loyal flock of the tribe. Your devotion pleases me today as well."

His Zhongyuan speech was flawless.

"Thank you Lord Nain Pureukdeok." 

Zhang Daein, the middle-aged man in charge of the tribute, answered with utmost deference.

It was hard to tell whether this was a Mongol raid or a tribute ceremony for some prince.

Though it was technically the latter, the way the barbarians treated it as a given was almost impressive.

Maybe the Jianping people had an innate sense of respect, given how naturally they also addressed her as 'Grand Supreme'.

"A fine day indeed. And doubly so for you, as I bring two pieces of good news."

"What might they be?"

"First, you no longer need to pay tribute. Our tribe has grown strong from your milk and wool. Though you are lowly creatures, barely above slaves, you have served us well."

"Thank you. Your words humble us."

Zhang Dae-in expressed gratitude even as the Mongol leader openly called them livestock.

In fact Zhang's face was radiant.

Outsiders might called it groveling.

But for Jianping's folks, this 'raid' was just a scripted performance from the very beginning.

But was it the same for the barbarians?

"The second good news is that you will have the honor of serving our tribe to the very end."

Confusion flickered across Elder Zhang's face but only briefly.

"Sheeps are truly remarkable creatures. The plains' master protects the weak and in return the sheep serve him all their lives. They give milk and wool, and when they grow old or injured, they willingly offer their flesh and hide."

If sheep could understand human speech they might protest.

'After providing all that milk and wool, is slaughter the only thanks we got?'

If even dumb animals would feel wronged, imagine how humans would.

"M-my lord what do you mean? We have served with all our hearts—"

"So we'll make sure to send you off peacefully."

The Mongols raised their weapons in unison.

Qing, who had come expecting some symbiotic exchange between Zhongyuan people and the barbarians, frowned.

\textit{Wait, isn't this a staged raid?}

\textit{Why did the mood just shift?}

"Kill the men and take the women! But if they're ugly just kill them too!"

Whether joking or serious, the Mongols burst into laughter.

Elder Zhang scrambled to his feet and blocked the leader's path.

"Wait wait! My lord! If the tribute is insufficient we can—"

"Hahaha! No need!"

Nain Pureukdeok laughed heartily before yanking his horse's reins.

The black steed reared up, and the leader's zhanmadao gleamed in the air.

The horse's front legs came down.

The huge blade of the zhanmadao, with the horse's momentum added, descended in a straight line toward Elder Zhang.

Elder Zhang only stared blankly as the blade filled his vision—

Clang!

The sharp ring of metal on metal.

The saber struck the ground with a heavy thud.

Elder Zhang fell backward and landed hard on his rear.

His tailbone should have been screaming in pain, but he was too stunned to react.

His head turned stiffly toward the blade, embedded inches into the frozen ground.

Only then did he realize how close he'd come to being split in half.

Gasping, he scrambled backward in terror.

Silence followed.

Nain Pureukdeok examined the dent in his saber and frowned.

Something had struck the blade mid-swing, so fast it had seemed like a streak of light.

He couldn't even tell what kind of hidden weapon it was.

Slowly he turned his head.

"Who's there?"

"What? A savage barbarian putting on airs? Just a passing beggar. What never seen one before? Don't Mongol bumpkins have beggars? Huh? Wait? Is it better to not have beggars?"

Nain Pureukdeok saw the beggar.

Their tattered clothes made their torso seem bloated, while their head looked oddly small.

Even stranger was the greasy hair covering their face, with glimpses of skin marred by hideous blisters and scars.

A diseased plague-ridden beggar, just looking at them felt contagious.

"What're you staring at? Never seen a beggar? Mongol bumpkins wouldn't know huh? How would wild monkeys living in tents know about beggars?"

Qing's tongue loosened.

"Beggars are parasites who don't works while living off others. They wander without a fixed home, pitching tents in some random corner and sleeping there. Oh, I see. You're in the same business huh? Mongol barbarians are the real beggars."

She grinned her white teeth, flashing beneath the beggar mask.

"Nice to meet you, fellow beggars."

"That's right! You are beggars!"

The little would-be beggar beside her echoed cheerfully.

'Would-be"' because his clothes were still too clean.

Qing smiled brightly at Nain Pureukdeok.

He clicked his tongue and jerked his chin.

"[Odeksain Sohyeok bring me her head—]"

"Wait! No violence! Violence bad! Safety good! Good! Good! Good!"

Qing waved her hands frantically.

"Let's talk like civilized people, huh? Typical barbarians, disagree and immediately go for the sword. Let's stop being barbarian and step into the age of civilization. You learned our language, if you don't use it now, when will you use it?"

"Beggar Sister?"

"Yes, I was rude earlier. I apologize. Uh what was it? [Sorry]—that's Mongol right? I know your language. Let's talk this out."

"Beggar Sister? What're you saying? They're bad barbarians invading our land."

"[Arhi jowayo. Boz, pliz drink.]"

"Beggar Sister? Are you listening?"

Murong Jun tugged at Qing's sleeve.

Qing ignored him, and continued butchering the foreign language, trying to appeal to Mongol pride.

"[Do you know the eyes of that time, Chinggis Khan? Dasinun Monggolul musihajwi mwora.]"

"Hello? Beggar Sister?"

"I'm a Mongol lover. Can't we resolve this peacefully?"

"Beggar Sister? Aren't you going to fight? They're bad guys…"

Suddenly Murong Jun's eyes widened.

It was because Warrior Lu had written characters on his back:

娘 民 逃 弛 默. 

Those characters means Lady People Escape Relax Silence. Putting them together, this is the meaning.

'Young Lady is stalling so the people can escape, so be silent.'

Murong Jun looked up at Qing with newfound admiration.

Of course whether Qing was actually stalling was purely Warrior Lu's assumption.

Only Qing knew her true intentions.

It could just be, as always, a pretext to provoke the opponent, a kneeling gesture to gain momentum.

But Nain Pureukdeok, unaware of these possibilities, relaxed slightly.

"Hmph. An interesting woman."

It was only natural.

People instinctively grew lenient toward foreigners who spoke their language

Especially when those foreigners praised their culture.

Qing's homeland was no different, they fawned over foreigners who clumsily said things like 'Kimchi good' or 'King Sejong best'.

"But. Talk it out you say?"

"That's right, it's the golden egg-laying duck. Or was it a goose? Huh? Anyway, have you heard the story of such bird? Once upon a time there was a duck that laid golden eggs…"

Nain Pureukdeok frowned but listened quietly to Qing's butchered story.

At this point, he was curious what nonsense this beggar would spout next.

It was the classic tale of the golden duck (actually goose) that lay golden eggs, which was known to everyone in Qing's homeland. It roughly went like this:

The farmer cut open the duck belly and ate it. It was delicious. Well, it was duck meat after all. End of story.

"So, what you're saying is since these guys will continue to pay tribute if we let them live, there is no need to kill them?"

"Right?"

"A fine tale. One worth passing down from the children of the meadow to the children of the steppe."

It was an expression of great praise in the Mongolian barbarian way: something that can be passed down from generation to generation,

Qing's expression blanked.

"Huh?"

\textit{Wait, this doesn't make sense.}

\textit{Did he actually get the moral of the story?}

\textit{But then again, maybe it made sense.}

\textit{The barbarians' Evil Karma isn't particularly high, barely over 100 points.}

\textit{At that level dialogue was possible.}

\textit{Perhaps the Karma system didn't count staged raids as evil.}

\textit{Aside of 'plundering' Jianping, what bad deeds could they have committed out in the empty plains?}

…Or so Qing thought until—

"But, woman. Isn't it ultimately up to the duck owner to decide whether to cut open the duck? The flock's master has chosen slaughtering the sheeps. Milk and wool no longer matter."

He was determined to spill blood.

"Wait, why are Jianping's people your flock?"

"Foolish words. Have you Han people forgotten history? Aren't you the lowest of slaves, lower than beasts? Yet we treated you as our flock, such mercy. And this is your gratitude?"

He was referencing the Yuan dynasty, when Great Khan ruled Zhongyuan and enslaved its people.

The Yuan Dynasty considered the Han people to be the lowest of the countless ethnic groups in Zhongyuan, and at that time they were treated worse than animals.

"A good tale deserves a reward, so I'll spare you. Now [Warriors of the steppe!] Hmm."

Nain Pureukdeok called his men then paused.

A wry smile followed.

"Ah, you cunning girl. The flock has fled. You were stalling."

"Stalling? For what?"

"Sheep, even if it runs away, will barely be able to bury its head in its pen. How can it possibly escape from the warrior of the steppe?"

"Why do you keep calling them sheep? You're making me crave lamb. Ah I want lamb ribs."

"Kehehe hahaha! A valiant effort, but you've sealed your fate. Had you been less hideous, I might have taken you as a wise and brave woman. Blame your own ugliness. [Odeksain Sohyeok, bring me her head.]"

Surprisingly Qing felt the same.

\textit{I was thinking of sparing him, but anyway.}

\textit{If this is the case, there's really nothing I can do. Really,}

\textit{It's not like I'm trying to get a taste of slaughter after a long time, nor is it because my hands are itching to kill after being too lenient with Jianping's people.}

\textit{Totally justified self-defense.}

Having a very convincing excuse, her grin stretched ear to ear.