\chapter{The Plague Ghost Hides Her Power (2)}

'I ardently wish you would not age.'

'But with that same ardor, I wish you would age.'

What poignant story could lie behind this intense ambivalence, this love-hate relationship?

However, this was a contradictory emotion that ordinary Zhongyuan people inherently harbored—

And the object of that emotion was the chickens they raised!

An old hen that no longer lays eggs fulfills its final duty through death.

The duty as a health food.

By being eaten by the owner who raised and fed it, it meets its tragic end, becoming one with the owner's nourishment, blood, and flesh, a perfect union of man and animal.

And most importantly, chicken was delicious!

So, Zhongyuan people await the aging of their pet chickens.

But the aging of a pet chicken means they can no longer eat those delicious eggs, so on the one hand, they wish the chicken would never age, proudly displaying its vitality with fresh eggs every day.

That's right.

Humans were such complex beings.

It's the same in Qing's homeland, don't office workers simultaneously feel the urge to quit their jobs and the desire to work until retirement to collect their severance pay and pension?

And today, Mr. Zhang's hen did not lay an egg.

Or perhaps it was yesterday.

That means today was whole roasted chicken day!

One might ask why there's such a fuss over just one chicken.

However, a chicken eaten at this poorest time of year, when one must survive on the income harvested in late autumn, was extraordinarily special.

In spring, one can gather wild vegetables or mushrooms, or go hunting.

But at the end of winter, for an ordinary farmer to eat a whole chicken is, in reality, quite a burden.

Of course, it's not an enormous burden.

But precisely because of that, it was a small but certain happiness in everyday life.

How wonderful it was to be able to boil a large chicken whole, put mouthfuls of meat into your mouth, and chew heartily.

After tearing off and eating as much meat as desired, the leftovers will be shredded, and then sticky rice will be added to the rich chicken broth, stirred, and made into a well-seasoned chicken porridge.

Thus, today was a truly long day for Mr. Zhang's family.

Why was the sun so long in winter, refusing to set?

And finally, his wife began cooking.

Shuiji (水雞) – literally, a dish where chicken was boiled in vegetable broth.

Shuiji, a traditional Zhongyuan dish, is made by boiling the broth cigorously, chicken was added, the fire was turned off, and it's left for about half a shichen to cook with residual heat.

This was primitive, ancient low-temperature cooking, in the style of Qing's hometown!

This was the difference from the Dongyi people's Baeksuk (boiled chicken), as it focuses more on the doneness of the chicken meat than on a rich broth.

So, Shuiji was a dish entirely focused on soft, easily chewable chicken meat, even the breast, without it being tough!

Thus, Mr. Zhang, Young Zhang, and Little Zhang, sat around the table, swallowing their saliva with gulping sounds, awaiting the wife.

But why was the wife not coming?

It was truly 一日不見，如隔三秋 (Yiri Bujian Ru Ge San Qiu)

It means that a moment, the time it takes to drink a cup of tea, feels like three autumns, or three years.

It was a phrase used when time seemed to stop due to anxious waiting.

As such, infinite, stopped time flowed by.

After a long wait, the wife finally appeared through the side door, carrying a large pot.

At last! Finally! At long last!

Chicken! It's chicken!

And so, Shuiji!

The old Zhang and the young Zhangs, their eyes wide with anticipation, were about to commence the combat-like dissection of the chicken—

It was that very moment.

Thump, thump, thump!

A loud knocking echoed from the door.

Mr. Zhang's hands, about to grab the chicken's limbs, froze, and then they looked at each other.

'Did anyone invite a friend today? Big one? Little one?'

'Not me.'

'Would I invite a friend on such an important day?'

'Then who is it? Who's so utterly rude as to knock on the door at such an hour?'

But bang, bang, bang! Bang, bang, bang!! Bang, bang, bang!!!

The knocking on the door grew louder and louder.

Mr. Zhang's expression soured completely.

\textit{Tsk, it tastes best when warm.}

\textit{Still, there must be some urgent business, otherwise, why would they be knocking on the door so fiercely at such an hour, as if to break it down?}

Mr. Zhang sighed deeply, got up, and opened the door.

And there she was.

"Hehehehe…"

A figure looking as if covered in tangled seaweed—

Her face completely obscured by tangled, greasy, unkempt hair.

But through the vertical fissure-like gap, a wide-open left eye, bloodshot and gleaming!

It was a terrifying moment that could have made people from Qing's hometown immediately stop breathing.

If Kayako, the most infamous Japanese ghost mother\footnote{Ju-On}, appeared, anyone's heart would sink.

Mr. Zhang was no different; the moment his eyes met that single eye filled with malevolence, he felt dizzy and his legs went weak, causing him to fall back on his bottom in sheer terror.

\textit{Is this a ghost, or is it a ghost!}

It was truly a sight terrifying to behold even in a dream!

"Gasp!"

"Grrr…"

With a growl like a hungry ghost from hell, the ghost leaped on all fours and lunged toward the dining table.

In Mr. Zhang's inverted vision, as he lay fallen with his neck bent backward, the ghost running on all fours, and the table glimpsed between its four limbs, seemed unusually large.

"No! Stop it!"

But it was already too late.

"Hiiieek…!"

"Aaaargh!!"

The wife's eyes widened, forgetting even to breathe, staring at the ghost as if looking away would mean death, trembling uncontrollably.

The eldest son, Young Zhang, shrieked, flailed, and then his chair tipped over with a creaking sound.

In the midst of this, the ghost, having landed on the table on all fours, greedily snatched the chicken from the pot with its grimy black hands and brought it to its mouth—

Little Zhang's pupils dilated.

The ghost's mouth gaped open.

How could a person's mouth open so wide? It was less like opening a mouth and more like the mouth tearing open and the lower jaw dropping.

Little Zhang's trousers rapidly darkened around the crotch.

Soon, the ghost began to tear into and devour the chicken whole.

No, 'shoving it in' would be a more accurate description than 'eating'.

Chomp, chomp, chomp, chomp! Chomp, chomp, chomp! Chomp, chomp, chomp, chomp, chomp!

The repulsive sound of food being stuffed into a wide-open maw and chewed loudly filled the surroundings.

The wife still frozen, Mr. Zhang groaning in agony from tailbone pain, Young Zhang flailing with his shins entangled in the chair legs, and Little Zhang still trembling uncontrollably even after emptying his bladder.

In the midst of all this, the ghost whispered softly.

"Hehe… Chicken tastyyyy…!"

At the foolish exclamation that shattered the terrifying atmosphere in one go, Mr. Zhang suddenly came to his senses.

Now that he looked, it wasn't a ghost, but a beggar woman—that plague ghost woman!

"You, you crazy plague ghost bitch…!"

Mr. Zhang sprang up and rushed to the table.

What met his eyes was the chicken, already three-tenths devoured in that short time.

In his haste, he instinctively grabbed the chicken held by the plague ghost—

\textit{Eek, how could a mere beggar woman have such strength…!}

Well, that plague ghost, Qing, was a master after all.

Even if not a master, Qing's physical strength already transcended human limits; without any exaggeration, in terms of pure physical strength alone, she was the best under heaven. It could be said that the expression 'a human being is strong'\footnote{MMA meme} was meant for Qing.

Mr. Zhang tried to snatch the chicken away, but like being dragged by a stubborn ox, he was pulled in without any resistance.

As the chicken went towards the plague ghost's mouth, Mr. Zhang's two hands holding the chicken were also pulled towards the plague ghost's mouth.

The plague ghost's maw gaped open.

As if to say, 'If you don't let go right now, I'll eat your fingers too.'

Mr. Zhang felt a chilling dread.

\textit{Surely, surely not. She wouldn't really bite, would she?}

However, Qing was a person who does what she has to do.

And then, chomp!

"Aaaargh!!"

Mr. Zhang screamed as his finger was bitten.

\textit{This crazy bitch! This crazy beggar is trying to chew and eat raw flesh! Crazy beggar! Crazy beggar!}

\textit{Ah, help! Someone save me!}

"Father!"

"Husband!"

At the patriarch's scream, Young Zhang and his wife frantically rushed to the table.

Young Zhang struggled to push his fingers into the plague ghost's mouth and pry it open, but there was not the slightest movement, as if trying to pry open a crack in a boulder.

Meanwhile, the wife grabbed the plague ghost's hair and pulled with all her might, but Qing's hair roots were superhumanly strong, and besides, hair was naturally difficult to pull out in clumps anyway.

"Gasp! Boohoohoo!!"

In this chaotic scene, Little Zhang, whose pants were thoroughly soaked, burst into tears.

Crying when one doesn't know what to do.

This was a characteristic of children.

And so, for a while, the grand battle between Mr. Zhang's family and the plague ghost continued, with the sorrowful sound of the child crying as background music.

"Waaah! Waaah! Wah! Waaaah…!"

With a 'whoosh' sound, the plague ghost's mouth opened, and Mr. Zhang and Young Zhang, who had been pulling hard on his hand, stumbled backward together, tumbling over the table with a crash.

"Husband!"

The terrified wife let go of the hair she was holding and rushed to her husband, now there was no one to disturb the plague ghost's meal.

\textit{This chicken is mine now. I can eat it as I please.}

"Waaah, ugh, waaaaaah…"

However, the sorrowful wailing awakened Qing's perfectly round conscience.

\textit{The father threw stones at the beggar, and his son watched and threw stones with him; that is exactly how children learn from their parents.}

\textit{But this little one wasn't there then, was he?}

Qing tore off a large piece of soft, moist, juicy brown meat from the relatively intact opposite side of the tattered Shuiji's thigh.

Then, she popped it into the crying child's mouth.

"Aaaah, chomp, ah, chomp, waaaaaah, chomp, chomp."

Even while crying, if something delicious enters their mouth, children must eat while crying.

This was also a characteristic of children.

Relieved of her guilt, Qing bit into the chicken, then ran out on all fours and disappeared.

Thus, at Mr. Zhang's dining table, Mr. Zhang lay fallen, with his eldest son and wife sitting around him, dumbfounded.

Chomp, chomp, huaaah, the sound of the child crying and eating.

"Husband, are you okay? Your hand, your hand is fine?"

After that, the wife and son's expressions were somehow strange.

He had screamed as if his finger was being severed, but when they finally pulled it out, it was perfectly fine, with just a mark.

"Ahem. That beggar woman, the plague ghost, seems to have gone completely insane. I'll punish her when it's light, but for now, let's just eat."

However, all that remained on the table were the ruined vegetable dishes that had been overturned and scattered when the plague ghost climbed on it.

And in the pot, only broth remained.

"…"

"…"

"…Sniff."

"Let's be thankful that at least the broth is left. Add some sticky rice, Wife. Let's shred some dried meat into it. Even so, the porridge will be a delicacy, won't it?"

"Haaah…"

It was at that moment.

Thump-thump-thump, nimble footsteps rapidly approached, and a black figure, like a swift beast, suddenly dashed in.

The plague ghost has returned!

"You, you crazy bitch…!"

"Oh, you're caught! Wait!"

Mr. Zhang and Young Zhang, who were picking up a chair with an angry expression, hastily shouted, 'Wait!'

The returned plague ghost squatted on the table and directly grabbed the pot.

Suddenly, the plague ghost grinned.

She grinned, showing white teeth like rice noodles, completely out of place for a beggar.

Then, she swung the pot at Mr. Zhang's family, and splash! Warm, lukewarm meat broth splattered all over them! It was unpleasantly doused all over their bodies.

"Heehee."

"You, you…!"

Just as Mr. Zhang was about to explode with rage, the beggar literally shot out like an arrow, running away on all fours, disappearing instantly.

What remained was a chaotic table, an empty pot, and a handful of chicken bones, perfectly stripped of meat, glistening and shiny, one couldn't tell when they were spat out.

"Gasp! Ugh! Waaaargh!"

Only the sorrowful wailing of Little Zhang, who had burst into tears again, filled the dining table.

This could be called the miserable and tragic end of one who threw stones at a beggar.

Plague ghost! How truly terrifying!