\chapter{The Plague Ghost Hides Her Power (8)}

The bodyguard of the young master of the Murong Clan, Warrior Lu\footnote{綠; lit. 'green'}, was a man who can barely speak due to a neck injury.

However, Warrior Lu had no regret.

For silence was the wisest course of action, and a man should speak not with his mouth but with his deeds, with silence!

To Warrior Lu who held this belief, the absence of a voice was but a minor inconvenience.

Just look at the fate of the Warrior Bai, who was demoted and transferred to the inner court with a pay cut, proof enough of the wisdom of silence.

Moreover, Warrior Lu has earned the trust of the Murong Clan Head, even daring to call himself the right-hand man.

The old saying from that Westerner with the hooked nose, 'Speech was silver silence was gold'\footnote{First recorded usage in English was in Thomas Carlyle's work, but the proverb itself came from Arabic}, was not wrong after all.

Though admittedly that Westerner hasn't even been born yet in this era.

But still.

As a bodyguard, Warrior Lu judged that the Beggar Sister, otherwise known as the Heavenly Blossom Sword, a master and a saint of Wulin, was already a remarkable martial artist even at her young age with a fully formed character.

In particular, her discussions on the difficulties of chivalry, judgment, and responsibility were so profound that even the Warrior Lu had to suppress his admiration.

Indeed, the young master himself was deeply lost in thought after hearing her words.

Previously, the Heavenly Blossom Sword had also enlightened the young master on the proper moral principles he should have known.

She was a benefactor who filled the gaps the family had neglected while being preoccupied with his Heavenly Martial Physique.

Though why she insisted on wandering around in the guise of a beggar every time they saw her remained a mystery.

Especially as a woman indulging in such disgraceful behavior that would make anyone cringed.

If you think about it, throughout history and folklore, those who transcend worldly glory and fame often wander as beggars.

The great minister of old, Taigong Wang was like that, as was Hua Tuo of the Three Kingdoms, and Confucius cherished beggars like brothers.

Even the Immortals in tales descended to the mortal world in the guise of beggars.

The Divine Maiden Sect was also part of the Daoist tradition, so perhaps at young age she had already attained great enlightenment and acted accordingly!

If Qing had heard this, she would have laughed awkwardly and nodded in embarrassment.

But people tend to see what they wanted to see.

Even when lying side by side, a disliked person would be thought of as lazy and pitiable, while a favored one would be seen as exhausted and in need of rest.

Even the silent Warrior Lu could not escape the limitation of being human, nso he was in what Qing's hometown would call a "bean-shell state".

Blindly adoring the Heavenly Blossom Sword and letting her do as she pleases.

Thus even when witnessing Qing's petty and vulgar revenge, he could only admire her inwardly.

\textit{At such a young age, she already possesses such magnanimity!}

\textit{After enduring such oppression, the proper way for a man would be to sever the enemy's head and settle the grudge.}

\textit{Yet she chooses to vent her frustration in a small-minded way, showing that while she may not be a man, she has the heart to embrace the world!}

Of course this interpretation was only possible because Qing was a master.

If a strong person forgoes revenge it's forgiveness, if a weak one does isn't it just giving up?.

Anyway.

Warrior Lu watched with satisfaction as the next generation of peerless masters—future heroes of Wulin interacted.

Why heroes? Because the young master though still a crouching dragon due to his youth, was destined for greatness with his Heavenly Martial Physique!

Look at him now.

"Peh pehh! That's dirty and cowardly!"

"Jun'er, in a life-or-death battle, what's dirty or cowardly? Are you going to tattle to King Yama after you die? 'If I'd fought fair and square I would've won, but I lost because of a cheap trick like sand in the eyes'. Would King Yama say 'Oh, what a shame' and bring you back to life?"

"But, it's underhanded!"

"Jun'er. No matter how dirty or cheap, survival comes first. Live long enough and you'll get your chance for revenge. And if you die honorably what about the people left behind? How sad would Elder Ilwolsangjae and Young Lady Murong be?"

"Well, but still…"

Qing helped Murong Jun up after he fell on his backside and dusted off his pants.

"If Jun'er don't want to use such methods, you don't have to. But you still need to know them. The unorthodox factions we'll face won't hesitate to use dirty tricks. So to become a true master, you have to experience all of them."

Murong Jun glanced at Warrior Lu for confirmation.

Warrior Lu nodded solemnly in agreement.

"Want to go another round?"

"Yes!"

Warrior Lu's eyes dripped with honey.

The Heavenly Blossom Sword was teaching the young master practical combat under the guise of sparring, not the rigid forms practiced in the clan, but something closer to real fighting.

And she was using all the dirty tricks of the Unorthodox factions.

It's an invaluable experience tailored to his level.

Qing was just playing around out of boredom, but her personality naturally inclined to tease children like a mischievous uncle.

But didn't the young master learn fast?

That's why Warrior Lu was so pleased.

At first the young master struggled with the rough savage nature of life-and-death combat.

But the Heavenly Martial Physique was no joke!

He's quickly adapting, proving the Murong Clan's young dragon, who can understand ten things when thaught one, was inching closer to his ascension.

The green-clad warrior was so proud he's practically giddy.

\textit{These two will one day compete for the title of the world's greatest master, what a perfect pair they make!}

\textit{How old is the Heavenly Blossom Sword this year? Twenty-three?}

\textit{The young master is twelve, an eleven-year gap, but in terms of zodiac cycles it's just one year gap. A perfect match!}

\textit{Especially since the young master having lost his mother early, so he will needs an older nurturing figure like the Mistress Heavenly Blossom Sword.}

Somehow Qing's title has now evolved to 'Misstress'.

But then again—

"Ah I'm not as spry as I used to be after all that running around. Must be getting old."

"Uh, Beggar Sister? I don't think you should just lie down like that."

"Jun'er, the earth is my bed, the sky my blanket. Where I lie is where I live. What does it matter how I lie? After sparring you rest, right?"

"Well…"

"Come here. Just lie down first."

"But Beggar Sister, you're a beggar, so it's okay for you to lie on the dirty ground."

"Then Jun'er can be a beggar too."

"But. beggars are dirty and smelly."

Murong Jun was brutally honest.

But Qing just laughed.

"But it's comfortable. That's why I sometimes choose to be a beggar. I can lie down wherever, eat without manners, laze around. No one will say anything."

"But, it's embarrassing."

"What, are you ashamed of your secret friend? Are you looking down on beggars now? Do the fifty million beggars of the world seem easy to you?"

"Well, a little?"

"Exactly. Beggars are like that. So you just avoid being caught, right?"

"Huh?"

"If Jun'er goes around acting like a beggar, no one will recognize him. If no one knows who you are, then it doesn’t matter how embarrassing it is, right?"

Murong Jun fell deep into thought.

Now that he thinks about it, it makes sense.

"You just don't know how good it is to be a beggar. Just lie down, stretch your limbs, and look up at the vast sky."

The obedient Murong Jun complied.

Lying down like that, he found it surprisingly comfortable. Though of course, lying was naturally more comfortable than standing.

But there's also a strange sense of liberation.

After rolling around, getting hit, and flying through the air during the spar, Murong Jun was drenched in sweat, his body heated from exertion.

The cold March ground seeps into his skin, cooling his overheated body with a refreshing chill.

"How is it secret friend? Not bad right? Being a beggar isn't so bad?"

"Uh, a little? But my head's uncomfortable. The ground's too hard."

"Hmm. Beginners might find it tough. Nothing to do about it, want to use my arm as a pillow?"

"Hehe, okay."

Murong Jun wriggled over, settling beside Qing, and resting his head on her arm.

A seasoned beggar lying sprawled out with a budding little beggar beside her.

A scene of perfect beggar corruption.

Warrior Lu's eyes trembled as he watches in real time.

The bodyguard of the young master of the Murong Clan, Warrior Lu, was a man who can barely speak due to a neck injury.

However, Warrior Lu had no regret.

…Until now.

For silence was the wisest course of action, and a man should speak not with his mouth but with his deeds, with silence!

To Warrior Lu who held this belief, the absence of a voice was but a minor inconvenience.

But never has the lack of a voice felt so frustrating.

Oh, well.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Why did Qing play with Murong Jun?

Of course out of boredom.

Why was she bored?

Because she was stuck in Jianping after clearing all past grudges.

Why was she stuck in Jianping?

To ensure the tavern owner who had added the crime of running away paid the price with an extended business suspension.

Though it's a bit awkward to resume her 'Jianping Gourmet Raid' now, especially since the Jianping folks have sworn off meat after having some stolen.

A fact Qing has known since her early days in Wulin, they were a stubborn bunch.

Others might found it absurd.

'What kind of nonsense is this? Stuck in Jianping with nothing to do, just harassing the tavern owner while complaining about boredom?'

But people were hypocrites.

Their own affairs were beautiful love stories, others' were dirty affairs.

In Zhongyuan it's called 我純他不 (Wo Cun Ta Bu). 'I am pure, he's not'. 

However, humans are inherently contradictory beings, like the Buddha.

Others' misfortunes hurt less than a splinter in your own finger, your family matters more than others.

Especially when it comes to the most important person, yourself.

So your own love was pure, others' was scandalous, this bias whether big or small was an unavoidable part of being human.

Qing just happened to be on the extreme end of that spectrum, a shameless brazen woman.

Anyway.

Bored as she was, it was only natural, as the sun rising and the moon setting, for Qing to go watch the 'legal' (not really) plundering by the barbarians.

Thus at the Jianping market square.

Goods destined for plunder were neatly stacked on carts ready to be taken away.

And from afar, the rhythmic clatter of many hooves grew closer.