\chapter{Telepathy (1)}

They say the Earthwood Goddess is leaving!

The goddess who overturned the Guangju Trading Hall, the specialty of Guangju, the special product of Guangju, the Earthwood Goddess who is the attraction itself of Guangju.

As such, every move she made became a topic of conversation.

They say that yesterday the goddess ate White Cloud Pig's Trotters, and they say that she ate the bones so cleanly that they shined like a mirror, so bright you could even see your own face in them.

They say that the bones, like a mirror, piled up to the height of a person's sternum, and that she must have eaten a dozen pigs using their front and back legs.

Normally, when rumors like this circulated, they would just scoff and mock it as ridiculous.

‘Did some beggar show up and lick all the bones clean?‘

‘A dozen pigs would be like eating forty-eight trotters, is that even human, is it a pig eating a pig,‘ they would joke and snicker like that.

But she was the Earthwood Goddess who cursed the cruel loan sharks to death, and who punished the tyrannical Guangju Trading Hall with her hammer.

The goddess, whose divine power and physical power were both efficacious, used that power to absolve most of the common people of Guangju from their debts.

After all, there weren't many ordinary people in Guangju who were free of debt from loan sharks during winter, and it wasn't like the Guangju Trading Hall wasn't selling the right to fish on credit.

As such, there were already several shrines in Guangju where models of shrines the size of small houses were built with wooden statues of the Earthwood Goddess enshrined.

So, what was the level of worship for the goddess like among the people of Guangju?

Right? Why would such a divine goddess eat White Cloud Pig Trotters for no reason? There must be some great meaning to it. Something about a menu fit for the workings of the heavens, right? A divine dish? A menu that matched her fortune?

Then, let us eat White Cloud Pig Trotters as well.

And just like that, Qing's dinner became a staple dish of the people of Guangju the next day, and White Cloud Pig Trotters, a boiled pork dish popular in Guangju, sold like hotcakes.

It was rumored that countless pigs shed tears because of it.

As such, people were listening closely to even the trivial conversations that the Earthwood Goddess had during her meals, in the hopes of perhaps hearing a single thread of heavenly secrets.

"Hey, sister. What is there in Huadu? Is there anything worth seeing?"

"Huadu? What's Huadu?"

"Hmm. I guess so……"

"I don't know! Ah, this is delicious."

"But why are you giving it all to me when it's delicious?"

"Hehe. I want my sister to eat a lot. By the way, why Huadu? Are you going there?"

"I have to go back. The architecture in Guangdong is pretty cool."

"When? Are you leaving right now?"

"I'm planning to depart after lunch tomorrow."

It was shocking news.

Of course, the common people who were eavesdropping secretly all perked their ears while their chopsticks flailed in the air, moving food towards their mouths whether they could see it or not.

Seeing the horrified gasps of the common people, Qing finally began her own proper meal without holding back.

Of course, the common people, once again, let out a series of gasps, praising the wonder of Qing's sincere eating.

And so, all the people of Guangju lined the streets that Qing would pass by on her way out.

It was a crowd large enough to make Qing think a festival was taking place if she didn't know better.

"What's going on? Is there some festival?"

Of course, since she didn't know, she asked.

"They say the Goddess is leaving!"

"What? You guys came out to see me off?"

Looking at the people who had gathered on both sides of the street as if they were watching some sort of parade, Qing's heart grew tender.

"Goddess! Please don't leave!"

"Goddess! Please come again! Next time, come visit our vegetable patch! I'll treat you to a feast!"

"Thank you so much! We will never forget you!"

"Thanks to you, my son is alive! I will pray for you to have a long and healthy life!"

One by one, they threw out such words and, hmm, it made her think if she had actually done that much to warrant this level of gratitude.

She didn't know she would receive such an enthusiastic response just for taking down one gang.

The common people had been suffering for so long.

The fact that the Earthwood Goddess was a down-to-earth and approachable person also played a role.

While she was leaving like that, a horde of punks blocked her path.

As soon as they saw Qing, they immediately knelt and tearfully pleaded, whether genuine or not.

"Aigo, Goddess, please don't leave like this. Please undo the curse, undo the curse before you leave!"

Looking at their Evil Karma, they definitely weren't decent guys.

What curse? Qing cocked her head.

Yeom Hwiyeong was so afraid of incurring Qing's hatred that he had meticulously investigated and carefully chosen which people to kill.

Thus, those loan sharks had yet to face his wrath.

"If you do a ritual, we will pay you however much silver and gold you want……"

"Ha, you're telling me to do a ritual to pray for evil people? What would I do with filthy, unclean silver and gold that are stained with blood and tears?"

"Goddess! We've done wrong, we've done wrong! If you could at least tell us how to avoid the curse before you go……"

It seemed like that curse was the work of her son-wannabe.

In the end, they were pleading for their lives.

The wrongs done as someone's life hangs in the balance are but a matter of regret and never repentance.

Regret and repentance were entirely different things.

Qing spoke in a fierce voice.

"If I don't tell you? You wanna try me?"

Qing raised her hammer.

At that, the thugs who had been standing in formation behind the loan sharks and blocking the way noticeably flinched, unable to hide their fear.

Although they had followed along out of obligation, what could they possibly do against the Earthwood Goddess who single-handedly obliterated the Guangju Trading Hall?

"The one who tied the knot must untie it. If you know that you've incurred hatred, you also know what created that hatred. So, you should deal with it yourselves! I've never seen such a spectacle before in my life."

"Goddess! Please don't do thi-"

Thwack!!!

In that moment, an illusion as if a mushroom-shaped cloud blossomed appeared.

Wrinkles formed on everyone's faces between their eyes. Ouch, that must hurt, they thought.

As she kneeled in front of her, unable to hold back any longer, Qing had finally administered a stern punishment with a head-splitting nuke noogie.

The loan shark writhed on the ground clutching his head, unable to let out a scream.

Even on her way out, the Earthwood Goddess was still doing some good.

Look at that vicious loan shark flailing about, unsure of what to do, they thought.

It was the very essence of refreshing clearness, the Clear Goddess in all her splendor.

And so, the Goddess left.

……But, wait?

……Is that right?

The people of Guangju felt strange.

Somehow, the guest of the Jin Clan, the Heavenly Flower Sword, seemed quite familiar.

They felt that they had somehow sensed the goddess's aura from the unfamiliar woman.

Of course, the Heavenly Flower Sword was a rising star of Jianghu, as well as a righteous dragon of the Orthodox Faction. An incredibly renowned female hero of Wulin.

Was there really a need to imitate the Earthwood Goddess? One could wonder about that.

At first, everyone was without thought.

Or rather, their thoughts were forcibly erased.

Because her stunning beauty was such that it made everyone's thoughts disappear upon merely looking at her.

They would just automatically stop in their tracks, gazing at her entranced, never getting tired of her beauty.

They fought over who was the most beautiful in Zhongyuan, but who even said that? She's the most beautiful in all the Central Plains!

When standing next to Miss Jin, Miss Jin looks ordinary, doesn't she?

Qing was originally elegant when her mouth was closed.

Though she was a beauty similar to a lily, a classical Zhongyuan beauty, Qing's beauty was in the higher echelon, with a smaller head and sharper features, a beauty whom those in Qing's homeworld would describe as the better version.

Of course, compared to Lily, who was famous for having the most complete bust of all the ages, Qing's massive mounds of flesh were just deemed vulgar.

But where had they seen those massive mounds of flesh?

She was quite tall, and the dramatic curve leading from her waist to her hips was familiar as well.

Where did we see such a marvelous, yet familiar figure with such a large drop in her waistline?

That familiar, almost déjà-vu like figure was mostly thanks to the specially designed Shaman Robes of Jin Seol, emphasizing the curves of the body.

Of course, in Jin Seol's aesthetics, a woman's clothing should accentuate the very best parts of the woman.

That's why Jin Seol always wore outfits that exposed the cleavage, whether it was the top, bottom, or middle, always revealing the deep valley in between.

And also, the fact that she always traveled with her sworn sister by her side.

The people of Guangju called that woman, who was the Heavenly Flower Sword's sworn sister, a temptress.

Why a temptress? She just looked like one at first glance.

She was a temptress whose face angered men.

She was the very personification of lewdness and obscenity!

Since these two people, with entirely different auras, traveled together, the people of Guangju who had become accustomed to Jin Seol's beauty and had eyeballs on top of their heads were also flocking to see another beautiful woman.

And above all, there was the way they ate!

How could two women exist in this world that ate, no, crammed food down like that?

The way they ate, not to enjoy the food, but as if they were just cramming food in their mouths with the sole purpose of swallowing it. At first, people admired how beautiful and blessed she was even as she ate like that, but.

Hmm, somehow, that feels like the Goddess, right?

But since she is pretending to be someone else, what could they do?

It's not like they were so foolish as to bring up a truth that she was trying to hide, and since they had also received grace, they should just pretend they didn't know, right?

In truth, it was doubtful if she even intended to hide it.

After all, what kind of Wulin female hero would roll up her sleeves and display the skill of a master carpenter during a reconstruction project?

A similar height. A similar demeanor.

A clueless sworn sister was always by her side.

She also associated with the Goddess's son frequently.

She's a skilled carpenter. She's laid back.

She eats like a madwoman.

Hmm. She must be the Goddess.

As such, as the reconstruction of the Jin Estate quickly proceeded and the building's outward appearance was preserved while its interior was completely renovated, little by little the miserable aura of the past was being erased. And as this happened, the people of Guangju solidified their beliefs from doubt, to suspicion, and to certainty.

And so, fifteen days after the Goddess returned.

The reconstruction of the Jin Estate was finally completed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While the Jin Estate held a banquet to celebrate the completion of the construction, a place with a somber atmosphere, akin to a funeral, existed elsewhere.

It was the Slaughter Moon Sect.

The Guangju heroes, the Blood Heroes, not Blood Heroes.

The people of Guangju were calling the bloodbath that had followed after the ones who rightly deserved to die by the name of heroes.

This "heroic deed" had led to the demise of the Guangju Trading Hall.

It wasn't just a simple demise, it was a meticulous massacre, tracking down and slaughtering the members of the organization one by one.

And the Golden Record Union also went bankrupt.

The owners of the Golden Hall, which was part of the Golden Record Union, were found dead in their homes every day, and those who were left were only a few who had become penniless after burning the debt records and distributing their assets.

Three evil factions that were set out to control Guangju…

That plan to pressure the Jin Clan and ensure they would never rise again, that plan to counter one family with three sects, had been turned to dust.

Instead of becoming the ruler of Guangju, they were in a position where they might have to abandon their signboard and flee.

Since the Jin Clan had declared that they would recruit warriors and disciples throughout Guangdong Province, they would soon regain the status of being the best in Guangju, even if it wasn't at the same level as its former glory when it was considered the best of Guangdong.

As such, Yi Wangchul, the Sect Leader of the Slaughter Moon Sect, was feeling incredibly anxious.

"Strategist Bang, what about the Blood Road Union? They said they cannot provide support?"

"Do not worry. I have already sent them a message, and the Blood Road Union's Gold Grade Combat Unit will be arriving soon to provide support."

"Oooh, Strategist Bang! As expected of you!"

The Gold Grade Combat Unit were the elites of the Blood Road Union.

If Yi Wangchul had possessed even a little bit of self-awareness, he would have realized that there was no way a Gold Grade Combat Unit would be formed to support just one Slaughter Moon Sect.

After all, even for the Blood Road Union, mobilizing their Gold Grade Combat Unit, made of chosen Masters from each affiliated sect, would require a major decision, consuming not just money, but also their influence.

But wasn't the support that the Blood Road Union had provided so far above ordinary?

They had sent him the Union's top strategist, and also sent him chests of elixirs while simultaneously telling him to interfere with the Jin Clan's recruitment efforts while expanding his own influence.

Having put in so much effort, shouldn't it be natural for the Blood Road Union to mobilize its Gold Grade Combat Unit to help him when his plan was in danger?

"Indeed, Strategist Bang is my Zhang Liang3!"

However, Yi Wangchul was sincere.

How grateful was he that he had bought an expensive writing brush and sent it to Strategist Bang's son, who was preparing for the civil service examination?

It wasn't just a gift that would have an immediate effect, he had even sent a late gift that would only be recognized once Strategist Bang returned to the Blood Road Union. This showed his gratitude for Yi Wangchul.

Of course, there was also a side where he wanted to appear in good light to Strategist Bang, the top strategist.

If the Strategist, who had the power to bring in chests of elixirs, did not forget this Yi Wangchul and the Slaughter Moon Sect after he returned, he had essentially given a bribe in advance to his son.

"If it wasn't for Strategist Bang, would I have been able to come this far? You are like, um, um, that is, the reincarnation of Zhang Liang, huh!"

Yi Wangchul praised Strategist Bang with a serious expression.

Strategist Bang had heard that Zhang Liang talk so much that his ears had practically calloused over.

Seriously, does this guy only know one strategist, Zhang Liang?
