\chapter{Telepathy (13)}

Originally, the youngest disciple of the Blood Moon School, Nan Doi, was not the type to particularly enjoy gourmet food.

With their meager living, what gourmet food could there be?

Just having plain rice to put in one's mouth, even if seasoned with a bit of seawater, was enough to think, ‘Ah, I can eat today', and be grateful for just being able to stave off hunger.

So, even amidst the checks and harassment from his Blood Moon School seniors, he was able to endure the harsh life of the youngest because at least the food was good.

Therefore, he had never thought of himself as having a particular fondness for food.

Even when food was served, perhaps because he couldn't eat meat very well, he didn't know if it was delicious or not. He would just let his fellow disciples eat and he would heartily eat the unpopular vegetable dishes.

Thinking about it now, it was truly foolish.

It wasn't that he didn't have a gluttonous desire for food.

It was just that he had never tasted truly delicious food, the real deal.

Human flesh!

Human flesh was so delicious that just the smell made his groin tingle with pleasure. He thought that even if he died eating it, it would be a good death, and that dying from deliciousness was what this saying was all about.

"Hmm. It's not enough."

Nan Doi smacked his lips.

There were levels even to the flesh of humans.

With his instincts, he could tell that the higher the martial arts prowess of the heart's owner, the more intense, deep, and rich the flavor of the meat.

These ordinary people, well, he ate them because he was hungry, but it wasn't particularly tasty, it wasn't tasty, it was tasty.

Nan Doi buried his face in the gaping hole where the heart used to be.

If one were to see him, they would be terrified, thinking he was trying to crawl inside the human body and wear the skin.

He practically buried his chin in the heartless torso, slurping up the juices. It was like the taste of rusted iron that had been soaked in the rain, a feast of the most exquisite flavors that was so utterly enchanting.

Suddenly, Nan Doi's ears perked up.

As he abruptly stood up, a thick blood vessel was caught in his mouth, pulled out, and stretched taut.

Chewing on what was in his mouth, Nan Doi sniffed the air.

This scent was the fragrance of a Master.

A fragrance that was hundreds of times more delicious than tasty commoners, a miraculous food that was already delicious yet could be even more so.

At this, Nan Doi staggered to his feet.

It was a shame to leave the half-eaten food, but there was no reason to eat the less tasty when the more delicious was available.

For the same reason, Nan Doi's fellow disciples slowly started to rise, wriggling.

The fellow disciples met each other's eyes.

There was a Master. A very strong Master. It would be delicious.

But it was too strong of a Master.

Then? They should join forces.

"I call dibs on the heart."

"Shut up, the heart is mine."

"Whoever eats it first gets it."

"I like the brain. It's soft."

"Good. One less competitor."

And then, with a Tap Tap Tap, they leaped forward all at once.

Screaming, the less tasty ones scattered.

It was extravagant to complain about the food, but after consuming the Masters, the remaining commoners were no different from easily catchable larvae that could barely resist.

Thus, the five Blood Ghouls crossed the street that was thrown into chaos from the screams, finally catching sight of their target.

There was a young man emitting an irresistibly fragrant scent, and a woman who emitted a less fragrant scent, yet looking at her appearance, she seemed to be a lascivious slut.

And in the middle was-

"Ugh."

The fellow disciples stopped simultaneously.

What, what was that?

The foul odor, hidden by the scent of a Master, surged into their lungs unfiltered.

It was like the smell of a pile of shellfish, oysters, and fish guts left to rot. It was the most unbearable stench, a rotten smell that was simply unbearable.

Nan Doi forced down the rising bile.

That, what, a living person, that was not a living thing.

The flesh, blood, tendons, and muscles that should have already died and decayed were held together in a seemingly intact form.

It was a sight incomprehensible to the senses of a Blood Ghoul, with every instinct and judgment of the brain screaming to look at that corpse. It was a terribly rotten end of something dead.

"Wow, fuck! The smell! I can't take it!"

Forget the scent of a Master, smelling it any longer would make them vomit the human flesh they had just swallowed.

The Blood Ghouls turned around at once and began to flee.

Upon encountering them, the group's appearance was that of people running away in fear.

Qing had just drawn the Moonlight Sword (No. 10) and was taking a stance.

If the people of Guangzhou had been more composed, they would have been amazed to see that the Divine Maiden knew how to use a sword.

They would have been surprised to see her draw a sword, thinking she only used hammers or pig's feet.

But the bastards, who had confidently rushed in, suddenly stopped as if they had hit an invisible wall, then turned around with rotten expressions and started running away.

And then, they met a crossroads and scattered in all directions.

"What the? Huiyeong, to the right! Heemaerangrang, to the left!"

Qing shouted as she hurried after them.

Heemaerangrang, the sound had a nice ring to it, didn't it? Anyway, since Yi-mei's skills were lacking, she should be sent together with Rangrang, who claimed to be a master.

Yan Hwi-yong is a grown-up who knows how to handle things on his own even if he is sent alone.

As I was chasing after the cannibal who was flying away with a bang, trampling the ground, I suddenly heard a noise next to me that caught my attention.

Langlang was able to run shoulder to shoulder with Cheong using a strange bouncy technique.

"Huh. Langlang. I said left? You have to help the weak Yi-mei."

“This Langlang can’t understand. You, Tianhuajian, are the weakest among the group.”

“Huh? What are you talking about?”

"The arrogant, gangster son of Tianhuajian is a master of the Profound Realm, and Tianhuajian's lecherous sister is at least the late stage Transcendent Realm. So the gangster is first, the nympho is second, and Tianhuajian is only third. You're so weak, so don't worry about others, Tianhuajian."

“Huh? Yi-mei is at late stage?”

“It is also presumed that she is facing the wall of Unrestrained Realm.”

“……? Huh, I guess I misunderstood.”

Qing shook her head.

How could something like that happen in this world, that Yi-mei is better than me?

That's ridiculous. It's a lie.

"But Tianhuajian, slow down. Why are you so quick-footed, you weakling? Langlang is becoming increasingly overwhelmed. Langlang's plan to rescue Tianhuajian from danger and be rewarded with a three-day banquet is about to fall through."

“Huh. If you want to follow, then follow me.”

As she stomped the ground, making the black mold, no, the Heaven-Shattering Demonic Qi, explode and send dusts flying, she wondered if this was what the Celestial Martial Emperor felt like when he performed his divine footwork.

The scene that the three trillion believers (estimated by the Heavenly Demon Cult, including believers of the past and future) have been longing for and revering in their dreams is the second coming of the Heavenly Demon using the Heavenly Reign method.

Actually, when it came to just running fast, it was more about brute force, using immense Inner Qi and leg strength to propel oneself.

However, a true master of Qinggong required a more exquisite ability, namely the vision to see the path ahead.

Having soared into the air by stomping the ground, Qing stepped on the awning pole of a shop and leaped onto the roof tiles to dash forward.

Then, with a swift jump, she kicked off the wall and landed lightly on the roof of the opposite building, skipping over buildings with each step as she unfolded Ximen Qing's maximum speed, displaying the terrifying flight of the Land Flight Technique.

Thus, having flown up, Qing made two turns before lightly landing on both feet.

Holding the handle of the sword with one hand, she spun it around and pointed it towards the sky. Then, she delivered a powerful vertical slash, and a satisfying sensation reached her hand.

The giant sword, entering from the shoulder and exiting through the groin, slammed into the ground with a thud!

The bisected Blood Ghoul spilled its contents and collapsed with a splat.

Witnessing the gruesome end of his fellow disciple, the other Blood Ghoul stumbled backward on his butt.

"Hieek, g-go away! Get lost!"

If the world was a peaceful place where telling someone to get lost made them actually get lost, that would be wonderful.

Qing smiled triumphantly, wondering how she should dismantle this one to maximize the satisfaction.

You bastards can run, but you're just like a fly on Buddha's palm. No, wait, if you're under it, then you wouldn't know how to get out of it even if you wanted to.

Should I just crush him? It's a good idea. Let's do it now.

Qing raised her hand, forming the shape of the Buddha's Palm, when suddenly!

Thwack! A strong force suddenly grabbed her ankle, causing Qing to be startled and jump in surprise.

"What the fuck?!"

"Bro… Run…"

It was the dying effort of the bisected Blood Ghoul.

With his one remaining arm, he desperately grabbed Qing's ankle, pulling himself closer, and then opened his maw wide to bite Qing's calf with all his might.

However, Qing's Protective Qi was forged by the Divine Maiden Sect through a particularly warm winter.

It was too much for mere teeth to penetrate.

At the very least, he needed to use Sword Force, and more precisely, he would have needed to be able to use Sword Compression to bite through Qing's flesh.

Startled for a moment.

What the? A zombie? Are there zombies in Zhongyuan?

Qing looked down at the Blood Ghoul that had bitten her just behind the ankle.

She felt a pressure as if someone was firmly massaging her.

"Ugh. Stinky feet. It smells like something's rotting……"

Qing's forehead creased with a frown.

Masters did not smell.

In particular, the physique of a Master who had mastered the Fairy Arts would have a fragrant scent of flowers, peaches, or other various scents depending on what they had learned. There should be no smell at all.

Stinky feet?

And not just any rotten smell, but a rotten oyster smell? Who is this bastard trying to frame?

"What? Are you trying to slander someone even as you are dying?"

"Uwek, uweeek……!"

But it seemed he didn't have the mind to answer, as the half-remaining Blood Ghoul vomited out what little contents he had left with the absence of his internal organs.

Agh, so dirty. Quickly pulling her foot away, Qing stabbed the back of the Blood Ghoul's neck with her sword.

The Blood Ghoul slumped over his vomit, twitching. What the? He still doesn't die like this?

Still, the movement of his torso had stopped, so Qing decided she would pickle this one in seawater later, going back and forth, back and forth.

Thanks to the tearful sacrifice of his fellow disciple, the remaining Blood Ghoul frantically ran away from the rotten stench monster.

However, he kept looking back, perhaps out of newfound gratitude for the fellow disciple who had sacrificed himself for him, even though they weren't particularly close.

That was when it happened.

"YAH!"

With a not-so-battle-cry-like, casual shout, there was a tremendous impact, as if being hit in the chest.

Rangrang, who had caught up to Qing belatedly with her peculiar bouncing footwork, kicked the Blood Ghoul with both feet while lying down.

It was only natural for Qing to cheer at the sight of the dazzling divine feat, reminiscent of her homeland.

As he watched the Blood Ghoul fly away, Qing firmly grasped the Moonlight Sword No. 10, an extra-large greatsword, with both hands as if holding a bat.

In an instant, four crescent moons were drawn in the air in the color of Sword Force.

Fourth Movement of the Yue Maiden Sword, Infinite Moonlight.

In the past, when she was just a pathetic Peak Realm, three crescent moons were her limit, but now, if she mixed in a killing move, she could manage up to six.

The Blood Ghoul's arms and legs were neatly severed and fell to the ground.

Qing grabbed the Blood Ghoul's chin and lifted him up, then looked around.

It was winter, so there were braziers placed here and there in the marketplace.

Qing heated both shoulders on the brazier, then roughly lifted him again and dropped his legless butt into the brazier.

It was a form of cauterization used by only the most macho of men.

"Uuuuugh!"

"Be quiet. This is medical treatment. You can't survive without stopping the bleeding, patient. Unfortunately, from now on, you're a eunuch. Your cock is being cooked all crispy and golden-brown."

"Uuuuugh!"

The Blood Ghoul desperately twisted his body, but what could a limbless person do?

Finally, after stopping all the bleeding, Qing grabbed the Blood Ghoul and dragged him on the ground, heading towards the rendezvous point.

Suddenly, Rangrang blocked Qing's way.

"Huh? Why?"

"Without any particular reason, I have a question for you. Is there a correlation between the extremely cruel form of incapacitation and the physical signs of excitement that appear in your body?"

"No? What? I just thought he wouldn't be able to run away like that since he was still alive. It's a waste of my time and effort to keep track of blood vessels and stop the bleeding, you know?"

"And why is that? Is it because the opponent is not human but a monster? Is that why you can enjoy tormenting it as much as you want?"

Rangrang's words made Qing's heart sink.

It was like stepping on a stair that wasn't there.

Qing tried to avoid eye contact, but Rangrang's attitude was resolute.

Ah shit, I didn't really want to think about this.

Qing tried to summarize it as simply as possible.

"Hmm. First of all, it's not because it's a monster. Even if it was a human, my treatment wouldn't be much different. He's a bad guy, you know?"

"A bad guy. This Rangrang finds it difficult to understand. Humans are beings with two sides, sometimes good and sometimes evil. Good and evil are concepts that cannot be clearly distinguished. Yet, how do you determine that the monster is a bad guy?"

"Well. If someone is eating innocent people, they're a bad guy, even if they're not a monster. Why do I have to explain this?"

"That monster is a ghoul. It cannot exist without an insatiable appetite for human flesh. From the ghoul's perspective, it's an unavoidable action for survival, but do you still call it a bad guy?"

"There's a problem with eating innocent people."

"Then, is a monster that only eats guilty people a good guy?"

At this, Qing paused.

Then she answered with a weak smile.

"If such a monster exists, at least I think it's very admirable and commendable. So, if, as a result, it's beneficial to the world, then even if it's a monster, shouldn't it be loved? At the very least, it should get some credit for effort."