\chapter{Telepathy (9)}

The name of the Wulin Alliance's regular combat unit that arrived at the Jin Family Estate was the Bamboo Chivalry Unit, named with the intention that they would practice chivalry straight like a bamboo.

A single unit of the Rising Star's Reserve Combat Team had tagged along as well for the purpose of traveling in Jianghu, but the main force was always the Bamboo Chivalry Unit's warriors.

In other words, the Crimson Dragon Squad was nothing more than a bonus.

It was for this reason that they were able to commit the atrocity of greeting the Jin Clan Lord on their first day of arrival, throwing their luggage down haphazardly, and rushing to the bar in a large group.

It was what one might expect from Rising Stars who had yet to grow up, or understand the world.

In fact, it was because they were truly immature.

What reason would there be for the young Rising Stars who had only trained within the walls of their sects to mature?

They were no different from children with only bigger bodies.

And the adults of the Orthodox Faction had also spent their youth in this manner.

As such, wasn't this the time where everything in Jianghu was new and fun? They could hold drinking parties after being freed from their boring sects.

Moreover, the Rising Stars had to be let loose like this from the beginning.

Just like how exhausted dogs, after playing to their hearts' content, would become docile, the Rising Stars also wouldn't cause trouble if they were allowed to play to their hearts' content.

They would rush in, enraged at the sight of something that met their eyes without considering the circumstances, or they would immediately point their swords at those who were branded as Demonic Adepts, or they would beat up corrupt officials because they were easy targets.

So even if their actions were infuriating, they were left alone with the thought that if they did not play now, when would they?

But then, a person urgently entered the Jin Family Estate, reporting that they were about to have a proper battle with the Blood Moon Sect on the rooftop of Jinhai Pavilion.

As such, the Jin Clan Lord and the Bamboo Chivalry Unit Captain, Biwhabul Weollyang took the lead, with the rest rushing to Jinhai Pavilion in droves.

And then it was all just ridiculous.

They came, they fought, and they won.

The shoulders of the Crimson Dragon Squad's Rising Stars, who had defeated those heinous and evil Blood Moon Sect bastards, rose up so high that they might just ascend to the heavens.

On top of that, thanks to the overwhelming gratitude of the special guests, a grand victory celebration was held, as they drank and drank.

By the time the Jin Clan Lord, Jin Clan warriors, the Bamboo Chivalry Unit Captain, and the Bamboo Chivalry Unit members rushed in, the atmosphere was already at its peak.

And naturally, they were scolded.

"Do you even have a functioning mind? How could you recklessly engage in a fight like that? What if someone had been hurt? How would you have taken responsibility? Are you all just individual people?! Even if someone was hurt and things ended with just being injured, that would be considered lucky. But what if someone was cut or sliced, or made into a cripple? What if someone had died? Would you still be so carefree and drink away?!"

At Weollyang's scolding, the Rising Stars, who had all knelt down, lowered their heads.

"You guys have absolutely no sense. Did you come here to play? To play? Right. You guys are gonna be working the night shift all the way until you leave."

However, the expressions of the Rising Stars were sullen.

They seemed to think that if they had ended the fight with just one injured member, they deserved this much of a celebration.

Moreover, that injured person had tripped over a roast duck while chasing after a Blood Moon Sect thug, and had cut his own cheek with his own sword.

He claimed that wasn't the case, but because there were so many eyewitnesses, he was summarily ignored.

It was just as Weollyang's eyebrows twitched, sensing the ominous atmosphere and about to unleash his rage, that Qing spoke.

"Great Senior, it was all my fault. The members of the Crimson Dragon Squad were only trying to help me, and because those bastards were making fun of my sworn sister and then used that as an excuse to harm her, I ended up acting first."

Qing's eyebrows drew a pitiful figure of eight.

It was a sorrow that melted the hearts of men.

However, Weollyang's epithet was Biwhabul.

If one knew that the epithet contained the word Buddha (佛), along with the Dharma name using the word Moon (月), they would know that he was a direct disciple of Shaolin with just a little knowledge.

He was already a direct disciple of Shaolin with deep Buddhist faith.

It meant he was not someone who would waver at the sight of beauty, except for his youngest disciple, who was still undergoing training.

Therefore, Qing's beauty had no effect on Weollyang!

Weollyang opened his mouth with a stern expression.

"Is that so. Then it can't be helped……"

However, Qing was not a stranger to Shaolin.

As the successor of the Buddha's Palm, the Heavenly Flower Sword was the benefactor who had restored that martial art to Shaolin.

Moreover, they had become familiar with each other on their way back to Shaolin after the Wulin Tournament.

The way Qing acted towards the adults was no ordinary matter, so he had already deemed her as a splendid pillar of the Orthodox Faction, to the extent that it was difficult to view her as just a Rising Star.

"Ahem, ahem, is it not something for Demonic Adepts to be consumed by lust for women? So how is your sworn sister doing? You do not need to feel any lingering grudges, I should say."

"I'm fine, Monk. They tried to take me away, so I destroyed them. Hehe……."

Gyeon Pohee replied with a carefree laugh.

An old person? No.

Then, someone Qing is familiar with? Yes.

As a result of logical thinking, Gyeon Pohee also showed respect.

"My sworn sister was only acting to protect the honor of a woman, but those bastards, in turn, acted so egregiously."

"That's the kind of thing those Demonic Adepts usually do."

"The members of the Crimson Dragon Squad only drew their swords to save this girl, so if you have any scolding to do, do it to me."

Weollyang's anger gradually subsided.

Seeing the woman she referred to as her sworn sister, it was obvious that she had an obscene and bewitching aura similar to that of Mara who had descended to the mortal world. As such, it was understandable for the scum of the Demonic Faction, who couldn't resist temptation, to be unable to hold themselves back.

Hmm. If family members were harassed, it couldn't be helped.

Since the Orthodox Faction was one big family, wasn't it only natural to help a member of the Orthodox Faction when they were in danger?

From that perspective, it wasn't right to criticize the immature Crimson Dragon Squad. Instead, they should be praised for their actions.

"No, it is not so if the Heavenly Flower Sword says so. Seeing as the Four Seas are One, you helped without hesitation in the affairs of Wulin's Orthodox Faction. It is something praiseworthy, not something to criticize. I will let go of the night shift duty."

At that, the eyes of the Rising Stars lit up.

As expected of the Heavenly Flower Sword! The Heavenly Flower Sword is the best!

I wish the Heavenly Flower Sword was our team leader.

At that, Jin Jagang, who had been a step back, let out a deep sigh.

Jin Jagang had already experienced the Heavenly Flower Sword's excuse of ‘I couldn't hold back and did it'.

Last time, she had said she couldn't hold back and beat those Demonic Adepts to death with a hammer, and this time, she had said she couldn't hold back and smashed the head of the Blood Moon Sect Leader.

With a pig feet, too. With a white foot that was as clean as White Cloud Reservoir.

She might look calm and friendly, but it seems that once her eyes flipped, she couldn't see a damn thing.

"That aside, what are all of you doing right now? If the enemy were to regroup and attack again, would you have faced them in this disarrayed, drunken state?"

"Hut."

The necks of the Rising Stars, which had suddenly become stiff, dropped down again like willow branches.

Now that they listened, what he said did make sense.

They had been celebrating and gorging themselves after having just won, but now that they thought about it, there was no guarantee that the enemy would just give up and back down after just one defeat.

While one could call them foolish, it was an immaturity that came from a lack of experience.

At that, Weollyang's eyes turned fierce again.

They were a support unit that came to help, but in front of the Jin Clan Lord, what a disgrace this was!

"Right, you bastards! Shouldn't you have come to report this incident and discuss what to do afterwards first? What are you all doing sprawled around as if everything is over! One victory and you think everything is finished!? Do you really think you can win if they all come at you at once!? You damn idiots, I'll make sure you don't cause any more trouble by keeping you locked on night shift! I can't have any peace of mind."

At that, the Rising Stars' shoulders slumped.

Qing hesitated for a moment and then decided that the sacrifice of a detestable person was necessary for the sake of the greatest happiness.

"Um….. I'm sorry to say, but even though we're a reserve combat team, we still have a format as a unit, so isn't it only natural to have the virtue of obedience to orders? As such, they probably couldn't act arbitrarily because they were just members of the team……"

"Eh? What is this? Come to think of it, where did Jo Hakchae go?"

What reason would she have to lie in such a safe place?

The members of the unit told the truth.

This was an honest confession, with no ulterior motives such as resentment that Jo Hakchae was trying to enjoy himself by running away with two women.

It was a confession based on their respect for a senior figure of the Orthodox Faction.

"What a bastard."

To think that the team leader had run away with two women, abandoning his responsibility to clean up after the mess.

"Ha. The Alliance Leader had asked to set his ways straight. Changbin, you will take over as the team leader during this dispatch. I will personally keep that bastard Jo by my side and set his ways straight."

Naturally, the flow of anger naturally turned towards the team leader.

At that, the Rising Stars felt a thousandfold sense of gratitude, engraving the three words, Heavenly Flower Sword, deeply in their hearts.

As expected of the Heavenly Flower Sword! I always believed in you!

From today on, I will follow the Heavenly Flower Sword as my older sister. Insulting the Heavenly Flower Sword is akin to insulting me.

Young Lady Ximen is the very embodiment of dazzling light, the words Wulin Six Flowers do not exist in this world. It is the Light of Five Suns, Ximen Light, no, Young Lady LightLightLight!

Anyone who saw this scene would think that the whole event was Qing's fault, and that she was just cleaning it up while gaining the favor of others.

However, Qing did not think that way.

It was the fault of the bastards who died because they were hitting on Hee Mae, not because Hee Mae was beautiful or because she had gone to the outhouse at the wrong time.

Qing was proud.

Thanks to this, the Rising Stars became happy.

Instead, Jo Hakchae would be unhappy.

This was the universal law of the world.

"You've played enough, so all of you go inside now. I have to keep watch to see when that bastard Jo will return."

Weollyang gritted his teeth.

At that, Qing thought.

It's a good thing the team leader's name is Jo, huh.

I do not feel one bit sorry for him.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It only took a single day for rumors about the incident at Jinhai Pavilion to spread.

This was because the stories that everyone wanted to talk about came from vivid and credible witnesses.

The guests that were using the VIP rooms were all people who were running their own businesses that they could be proud of.

And the testimonies from those people were already the truth in itself.

If you were to object and say they were lying, you could be financially isolated, creating a catastrophic disaster for yourself.

And thus, the shocking news was told.

The Blood Moon Sect Leader was dead!

And he had died from being hit by a pig's trotter!

His head was smashed by the pride of Guangdong, the White Cloud Reservoir Trotter!

No, wait, who smashed his head?

The Divine Maiden, no, the Earthwork Fairy, no, the Heavenly Flower Sword!

The fact that the Heavenly Flower Sword's identity was that of the Earthwork Fairy was a truth that everyone was just pretending not to know.

If Qing heard this, she would probably be dumbfounded and wonder why it was the opposite. That the Earthwork Fairy was the Heavenly Flower Sword.

It just so happened that the people of Guangdong were more familiar with the Divine Maiden, who had been talking to them and mingling with them. So it couldn't be helped.

Just as the entire Crimson Dragon Squad had become happy after just one Jo Hakchae became unhappy, all the members of Guangzhou had become happy after three major forces of the Unorthodox Faction became unhappy.

However, it was unavoidable that the unhappy parties, particularly the only survivors of this incident, the Blood Moon Sect (since the other two had been destroyed), were grinding their teeth.

"We have to report this to the Unorthodox Alliance and declare them as official enemies of the Unorthodox Faction! I will go inform them of this tragic incident with tears!"

"It's not a tragic incident, uh, well, it's not tragic! Are you going to send such an idiot!? I, your younger brother, will go."

"No, Sect Leader! Please leave it to me, this younger brother! I shall return after informing them of this monstrous atrocity!"

Everyone was clamoring to go and inform the Unorthodox Alliance.

Wang Woo's expression was sour.

After all, since they didn't know when the Orthodox Faction would attack, they were basically saying that they would run away to inform the Unorthodox Alliance.

If they returned with the Unorthodox Alliance's support and their sect was destroyed, they would just look for other jobs, and if it was not destroyed, they could strut around saying they brought the Unorthodox Alliance's support.

Therefore, everyone was suddenly overcome by a sense of loyalty and rage, clamoring to be sent.

"Chosu, you will go."

"Yes, Elder Brother."

"Elder Brother! Why must it be Chosu!? Isn't it more fitting for someone of greater rank to go so that the Unorthodox Alliance will listen to us!?"

"Are you seriously asking that?"

At that, the younger brothers closed their mouths.

Chosu the Snitch. He was an expert at reporting to higher-ups, so his nickname was ‘Snitch'.

Even when he did wrong, he would cry, sob, and wail, claiming he was wronged, while ignoring the events that transpired and rewriting history.

"Anyway, during our Big Brother's funeral, the Orthodox Faction will not be able to attack. In the meantime, gather all the children. And bring all those remaining at Guangzou Vanguard and Golden Treasure Gate as well. Since they have nowhere else to go, they'll come willingly."

Wang Woo's eyes gleamed.

Crisis was also an opportunity.

If they could get past this situation smoothly, the entire Blood Moon Sect would fall under Wang Woo's control.

For now, they would delay it by holding a funeral for the previous Sect Leader, and then lower themselves and apologize to buy some time, the Unorthodox Alliance would never turn away, for sure.

They wouldn't want to throw away the efforts they had put into dispatching their Chief Advisor and sending chests of elixirs.

Before that, he needed to first tighten the internal security.

Wang Woo placed a chest in front of the remaining Blood Moon Sect leaders.

"Here. These are elixirs sent from the Unorthodox Alliance. They were originally for the youngest, but since the sect is in a difficult situation, wouldn't it be better if we ate them and raised our realms immediately?"

Elixirs! Elixirs sent from the Unorthodox Alliance!

Those elixirs that the Chief Strategist would never give, even if they were begged or threatened!

Forgetting the immediate threat, the eyes of the Blood Moon Sect leaders gleamed with greed.