\chapter{Telepathy (14)}

Rangrang still vividly remembers that day.

The day her family home burned down. The screams, the blood, her mother, her father, and the burning heat of a blade piercing her stomach.

Hey, you bastard, how can you just stab her like that? She's a looker, so let's have some fun before we finish her off.

Why, you want to have a taste now?

You have a hobby of screwing corpses? Once there's a hole in the belly, it's all loose and won't feel good. I thought I could finally get my hands on a nobleman's daughter.

Rangrang couldn't understand.

Why? What did I do wrong?

And why isn't anyone helping me?

Everyone smiled at me and thanked me, saying I had the heart of a fairy, that everyone in Jilin would be grateful to me.

Why? Isn't anyone helping me?

I need help. It's not fair, you traitors.

And then there was that person.

Amidst the burning world, she stood alone, pale and elegant.

"Oh my. I came because I smelled the scent of the Secret Sect. Are there sorcerers in the Imperial Palace now? But it's so clumsy. Young Lady? How is your body? It would be a waste for such a constitution to just die."

"Help, please. Save me."

"Oh dear. I'm sorry. I can help you, but I can't save you. I don't know how to save people, and I don't want to know. What if you could live as a monster instead of a human?"

"Yes, help, please, I don't want to die."

The person smiled gracefully.

"Then, take a deep breath and die. When you wake up, the world will have changed."

And so, Ha Hu Rangrang died.

Even now, when she closed her eyes, she could vividly feel the sensation of that moment, the cool comfort of sinking into black water.

And then Rangrang opened her eyes.

The first thought that came to mind as soon as she regained consciousness was, Ah, I'm no longer human.

But I'm alive.

I survived.

The foolishly kind-hearted Ha Hu Rangrang, who was used and discarded, was gone.

Now Rangrang would live for Rangrang!

Rangrang's determination!

"So, what should Rangrang do now?"

"Nothing?"

"Why? Usually, at times like this, people threaten you by holding onto your lifeline. Like, if you value your newly revived life, you should listen to me?"

The person just smiled gently.

"You are free. Occasionally, I might ask you for a favor. But if you don't listen, I'll just be a little sad? Hiiing. I spent four nights awake and poured in a hundred gold ingots, yet you are so heartless, sob sob."

"Why? Then why did you save Rangrang?"

The person's smile deepened.

"We are the only family each other has in this world? You might not understand it yet, but you will someday. Monsters who can never coexist, well, um. You'll truly understand only when you realize it yourself, right? So for now, enjoy the pleasures of life that you haven't been able to experience to your heart's content?"

And then, as if suddenly remembering.

"Ah. Right. I've hidden various convenient functions in your body? If you twist and pull out your left pinky, ta-da. A fire starter. It's a new feature that lets you start a fire anywhere?"

"…!?"

Rangrang was startled and twisted her pinky.

But the pinky was firmly attached.

A clear laughter spread through the air.

"It's a joke. You're so naive. But if you really want it, just tell me? I can put a liquor pouch in your chest. But when the liquor runs out, it'll shrivel up, so, pfft, Su'a used that, and, hahahaha, haaaa. Alright. I can't recommend it."

"I don't need it. That kind of function."

"What about a blade coming out when you pull out your forearm?"

"I do not need it."

"Then, do you wish for revenge for your family?"

Rangrang hesitated.

"The Imperial Family will take care of it eventually, but I'm curious to see how they'll do it, so I'm looking forward to it? I'm sorry, but you'll have to wait a bit."

At this, Rangrang hesitated for a long time, then finally gave her answer.

"It doesn't matter. It's no longer my, Rangrang's, concern."

"Rangrang?"

At the sound of her name, Rangrang suddenly came to her senses.

"Ah. Where were we? I was talking about a monster called a Blood Fiend, or a Blood Ghoul for short. Did I mention that?"

Rangrang's identity was vouched for by Jo Hakche.

Jo Hakche quietly asked.

"Young Lady, are they similar to jiangshis?"

"They are much inferior to jiangshis. Comparing Blood Fiends to jiangshis would be like comparing an earthworm to a human, or a candle to the sun. It's an insult to the higher-level jiangshis. So, you should apologize to Rangrang immediately."

"…?"

"Ahem. Anyway. Incomplete Blood Fiends are just ghouls, inferior monsters that can't even control their appetite. All their actions are driven by the desire to eat human flesh."

Rangrang sighed and got to the point.

"There is no way to turn a Blood Fiend back into a human."

At this, sighs of despair erupted.

At the first rallying point, captured Blood Fiends were tightly bound, and the surviving members of the Exterminating Moon Squad were being closely guarded.

Even if they were called Blood Fiends, they were incomplete, and their realm was at best around the Peak Realm.

Of course, it was only three months.

In just three months, they had raised young men with hardened bones, who were late to start cultivating, to the Peak Realm.

This was why the Blood Cult was so obsessed with creating monsters.

Twenty Peak Realm Masters could be considered a sufficient force, but they were all driven mad by the desire to eat human flesh, each according to their own tastes.

This meant that it wasn't difficult for the Wulin Alliance's combat squads, organized in groups of five, to subdue them.

Moreover, since there were horrific screams coming from everywhere they went, it was easy to track the Blood Fiends' locations.

At this, Jin Clan Lord, Jin Jaggang, approached Wang Wu, who was lying on the ground, covered in blood. He was the former Head Manager of the Exterminating Moon Squad, now acting as the temporary Sect Leader.

They were not injuries inflicted by Orthodox martial artists.

There were wounds all over his body, with clothes torn and flesh ripped off, so it was more accurate to say that the Orthodox martial artists had saved Wang Wu from the Blood Fiends.

"Do you have anything to say for yourself?"

"Unfair! It's unfair! I really didn't know. All the new disciples were managed by Secretary Bang, the Chief Secretary of the Fourth Lord's Alliance, Bang Jeommyeong!"

"You need to choose your words carefully. With your own mouth, you're essentially accusing the Fourth Lord's Alliance of creating evil monsters of the Blood Cult."

Wang Wu hesitated.

But he was truly wronged.

Fourth Lord's Alliance, my ass, you Fourth Path Alliance bastards!

You deceived us and used our sect!

He gritted his teeth without realizing it, feeling a surge of anger.

"It's true! The Fourth Path Alliance sent a box of elixirs and Secretary Bang! They said they would support our sect with twenty martial artists, fifteen each for the Golden Dagger Clan and the Gwangju Boat Clan, and fifty more later!"

This was why the Jin Clan couldn't recruit disciples.

They had already recruited fifty with the elixirs, and they were going to gather another fifty later.

The youths of Gwangju were eagerly awaiting the next recruitment by the Fourth Path.

At this, Jin Jaggang and the Shaolin disciple Wolryang, the combat squad leader, exchanged glances.

This was no ordinary matter.

Rumors had been circulating that every city where the Blood Cult had wreaked havoc, the bastards of the Fourth Path Alliance had sent support and taken over the territory.

What if the Fourth Path Alliance had joined hands with the Blood Cult?

Was the long-standing peace of Wulin truly about to be shattered?

"First, break their arms and legs to subdue them. Hmm. It would be best to transport them to the Alliance."

At this, Orthodox martial artists stepped forward with their scabbards or dao sheaths.

"J-Just a little more, just a little more!"

The Blood Fiends did not show any signs of fear, but rather drooled and smacked their lips.

It was then.

"Oh my, sirs! Please don't! There must be some mistake, some misunderstanding! Haseong is not that kind of child, he's such a good boy……!"

Among the crowd, an old woman ran out and covered her son, pleading with a tearful voice.

She begged and pleaded, even kneeling and clasping her hands together. She said he was such a good kid and couldn't possibly have done such a thing. She begged them to be lenient, saying she was an old woman who only had her son to rely on. She even offered to take his place.

"Madam, please step aside. Your son has already."

"Oh my, sirs! If he did something wrong, I'll scold him severely. I'll even take him to the magistrate's office and have him beaten with a cane. This old woman only has this son to live for, so if you do this, what am I to do? Please, just kill me instead, you bastards, aigo, what are you doing? Kneel down right now! Quickly! Say you were wrong! Hurry up and beg!"

As the woman spoke, she tried to grab her son's hair, but at that moment…

The son, Haseong's, eyes flashed, and he suddenly stretched his neck and lunged at his mother.

He bit into his mother's neck and, with her, fell to the ground, burying his head in the wound.

Gulp, gulp, the sound of liquid going down his throat was as loud as thunder.

"Damn it! Stop him!"

"Pull them apart immediately!"

The Orthodox martial artists grabbed the bound limbs and struggled to pull them apart, causing the mother's neck to stretch grotesquely along the muscle fibers, connecting to her son's mouth and teeth.

"Heuheuk, it's tasty, Mother, keuheuk, I'm sorry, but it's so tasty, let go! Let go! Mother!"

The Blood Fiend seemed to laugh and cry at the same time, making a loud, ambiguous noise.

The Orthodox martial artists, lying on the ground, struggled, shouting ‘Mother, let go, mine, my mother' in a vicious voice.

Qing rushed to the woman.

Her neck was torn open.

If it had been a clean cut with a sword, it might have been possible to save her, but with a human's teeth tearing through her flesh, there was nothing that could be done.

"Gasp, gaaasp."

Qing shoved her hand into the wound, grabbing the blood vessels above and below and covering the windpipe with her palm.

It was so that she could at least say her last words on her way out.

"My, son, son, Mother is fine, sirs, please, forgive, please, forgive. My child is originally good, he's good………"

The woman's focus blurred and she passed away.

Qing quietly stood up.

Thud, thud. Qing slowly walked forward.

"The smell! Keuaaak! The smell! What is this smell! My nose! Get it away, move it away!"

"Young Lady Ximen?"

Hmm. It seems like the child was originally a piece of shit since birth.

I thought all children were precious in the eyes of their parents, no matter what others thought?

They say that even if others see them as a scoundrel, to their mother, they are just a good kid who made bad friends.

Maybe he was led astray because he made friends with those Blood Cult bastards.

Or what if he really was a good kid originally?

What if he became a Blood Fiend and couldn't overcome the monster's nature?

What does it matter?

What's done is done, and if I had just cut his throat earlier, an innocent mother wouldn't have had to go to the afterlife.

Suddenly, Qing felt a sense of relief, an inexplicable comfort, and even felt a bit better.

Oh right. Now I see. There are fuckers in this world that I can just kill without thinking.

Bastards that can be burned alive, smashed, twisted, and crushed.

"Keok."

The huge blade of the Moonlight Sword No. 10 pierced the back of the monster's neck.

"I should have known you would do this. I wanted to smash you bit by bit from the fingertips, but."

Since he was such a terrible son to his mother before he died, it wouldn't be bad to let him die comfortably, considering his dead mother's wishes.

And then, a proper silence finally settled in the square.

The traits of the monster, which were only heard in descriptions, the ghoul that could not control its appetite and had no sense of reason.

A monster that could not return to being human.

Only after seeing the ghoul devour its own mother did Rangrang's explanation truly sink in. 