\chapter{Telepathy (2)}

Fang, the strategist, was receiving the utmost hospitality from the Sect Leader.

However, compared to that utmost hospitality, his reputation within the Moon Slaughtering Sect was not good.

Of course, it was partially the fault of Wang Wu, the former chief administrator (who was eventually demoted) who created and spread all sorts of bad rumors, but the main reason was that he simply didn't fit in with the other sect members.

Originally, in the Unorthodox Faction, hanging out with other sect members meant only drinking and whoring.

They did not engage in petty, effeminate social activities such as chatting and sipping tea like those of the Orthodox Faction.

It was the virtue of the Unorthodox Faction to build friendships and strengthen bonds between brothers over drinks, whoring, and enjoying their free spirits.

So, it was inevitable that Fang, who had a concubine from the start and never showed up to any parties held at night, would remain an outcast.

But this was not something from the past. It was the same in the future, in Qing's homeworld.

It was an act of rebellion akin to not going to welcome parties, eating alone, not joining any company dinners, or not joining a farming clan in a small to medium-sized company.

Though she did not know about large corporations, she expected it to be similar because people living in that world also shared similar mannerisms.

Therefore, what would Fang, whose rumors only intensified due to the sense of alienation, be described as?

That he engaged in homosexual activities. Or that the honorable and high-ranking strategist of the Asura Association did not wish to associate with the trash of a small- to medium-sized faction like the Moon Slaughtering Sect. Or that whenever he opened his mouth, he would say that the Asura Association looked down on the Moon Slaughtering Sect as if it was nothing but shit.

From Fang's point of view, it was irrational.

Fang felt wronged.

Fang, too, liked women! He liked drinking!

But he simply couldn't do it!

Why?

"Langrang, I have a real favor to ask. Just one drink with the Moon Slaughtering Sect Leader today, okay? Just one."

It was a ridiculous sight of the Asura Association Strategist clinging onto her, begging.

However, the servant answered with a blank face that held not even a hint of emotion, sending a chill down one's spine.

"Impossible."

"No, but, why, huh?"

"Alcohol is the root of all evil. We cannot risk mistakes or misstatements caused by intoxication."

"But that's why I'm saying we should only have one drink!"

"You may drink it here. Shall I bring the liquor?"

"No, that's not what I'm saying. You know that drinking alone would be boring. Right?"

"Shall I pour it for you?"

"And to think that this is also an extension of carrying out a mission. You know this too, right? That I'm an outcast in the Moon Slaughtering Sect. For men to build proper friendships, we have to eat and drink together, play with women, and have naked conversations in order to create strong bonds. Isn't that so?"

"I prefer our current level of distance. If you wish to play with women, you may play with me."

"No, I mean play with women as well."

"Do you wish that now?"

At this, Langrang abruptly lowered her clothes.

Fang sighed deeply, frowned, and shook his head.

The combination of man and woman was a communion of sorts, but the sight of Langrang's terrifyingly blank face would instantly cause one's thing to lose its vigor.

Moreover, her skin was icy, cold, and inelastic, so any pressure would leave a visible mark.

No matter how desperate for a woman one may be, no man would ever embrace such a woman.

It was a woman who wouldn't even flinch even if stabbed by a knife, no, a woman who actually wouldn't flinch even if stabbed by a knife or burned by fire.

"Just one drink, okay? Just one?"

At that, Langrang raised her head and looked at the sky.

Fang felt hope after a long time.

It was because it was a reaction that she showed when she was lost in her own thoughts.

Fang swallowed and waited for Langrang's decision.

How long had it passed?

Langrang looked at Fang again.

"Understood. The possibility of mistakes due to intoxication is very high, but I assess that we can expect the fostering of camaraderie and the improvement of human relations as a result. But you must not drink more than one bottle of liquor."

"Yes, I'll only have one bottle. Wasn't the problem with the liquor itself? As you said, it's to foster camaraderie! Just wait, you have nothing to worry about."

Fang's face brightened up as he quickly put on his outer coat.

He was thinking of running over to the Sect Leader to demand, or rather, beg that they should hang out intensely and authentically today.

Just as he was putting on his clothes and about to run out, Langrang stopped Fang.

"Wait a moment."

"What is it? Why? You know that what's done is done? You already said it was fine? You can't change your mind now-"

"It's a message."

At that, Fang's expression changed drastically.

His face turned ashen as he knelt in front of Langrang, bowed his head, and spoke respectfully.

"While lying lazily on a chair and stroking a woman's body. Did you hear from that bastard? Ah, you did? No, don't convey this, hmm. Yes, you, my disciple."

"This unworthy disciple greets the sole noble and revered Heart-Stealing Demon King."

"While doing a respectful bow. This unworthy disciple greets the sole noble and revered Heart-Stealing Demon King."

Langrang relayed Fang's actions and words.

Then, after a brief moment, Langrang opened her mouth again and spoke.

"While stroking a woman's breast. Yes, how far has the great work progressed? How many Blood Devils are there, excluding the Jinjeok Gang and Gwangju Buddhist Monks?"

"With a dumbfounded expression. Why are you still attached to that ‘word'? Do you think that makes any sense? Or are you going to start speaking with ‘words' after you've pissed yourself?"

"While yelling in anger. No, you fucker! I'm talking to you! This useless thing. You can't even properly deliver messages. Should I change you to something less useless? And that bitch, Un'ga, is going around playing with those Mongol bastards."

Fang quietly waited for her to finish talking.

"While turning the anger away pointlessly. What's wrong? Why aren't you answering? When will the Blood Devils be complete and how many are there?"

"There's about 20 and they will be complete after you feed them the Ten Hearts three days from now, Great Demon King."

"While glaring and then shaking his head. I've sent five hundred hearts and there's only twenty? Ha. Well, whatever. It's always been like this, that you'd get fucked over if you accidentally bump into the wrong bastard. I shall not blame my disciple."

"My Teacher's mercy is as wide as the ocean."

"While snickering. You little shit, what's with that flattery? Enough with empty words. Do it well, okay? You know they can't be controlled if they take the Ten Hearts? Don't go looking around elsewhere and stay close and finish it. That's all. Disconnect."

At that, Fang finally raised his head.

Langrang, who had been looking down at Fang with a blank face, casually threw out a single word.

"The Heart-Eating Demon King told you not to be looking elsewhere. Yet, you intend to indulge in debaucherous sex with many others while drinking alcohol?"

Even when she chose how to express things, she somehow always ended up like this.

Fang frowned and spoke.

"Did you not say that there is no changing your mind now?"

"I do not listen to the orders of the Heart-Eating Demon King. I was only assigned to perform the task of a messenger for the Heart-Eating Demon King and the task of being a weak bodyguard for you, according to the orders of my master."

"Ahem, weak bodyguard, she says."

Fang frowned and grumbled.

And then, he stopped as he was about to cross the threshold.

His teacher had also asked him to try to endure it for a few days, or should he go and enjoy the licentious banquet that had been permitted for the first time ever in Guangzhou.

But he had already endured it for too long.

Unwilling to fight against the desire that had surpassed his control, Fang eventually crossed the threshold and disappeared.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Two days after the construction of the Jin Family Estate was complete, the support unit of the Wulin Alliance arrived.

They had been on the verge of having to host their guests outside due to the smell of rotting corpses, so their arrival was very timely.

Thus, the combat unit that went to Nanning in Guangxi Province and then directly headed to Guangzhou in Guangdong Province was now entering the refurbished Jin Family Estate.

After greeting the clan head, the combat unit unpacked their belongings and Qing wandered around the Jin Family's reception hall, wondering if there would be any familiar faces.

"Did you all hear what Clan Head Jin said? From tomorrow onward, our Hwaryong Team will be helping Jin Clan manage their business areas. Although I am sorry that we must start working right after such a long journey, isn't this exactly what friendship in the Orthodox Wulin means? Right? We help each other when things are tough! Then everyone will help me too when I'm having a hard time! That's the Murim Alliance spirit, you and I become us! The Jin Family is not a stranger! Right?!"

"That's right!"

"Yeah, we're all one family in the Orthodox Wulin! We do not need to make detailed calculations or consider any ulterior motives when helping each other! Is that right?!"

"That's correct!"

"But! Tonight is our freedom! Do you understand what this means?! It means that this big brother will be treating all his brothers to a night that will make our noses crooked! Even though we have work tomorrow, so we have to dispel the intoxication with Inner Qi, we cannot give up the genuine brotherhood between men! Right?!"

"Brother Cho! Brother Cho! Brother Cho!"

"Tonight, we will drink ‘till we die at Jinhae Pavilion!"

"Woooooah!! Brother Cho! Brother Cho! Brother Cho!"

The scene was nothing short of a scene of utter madness, as excited youths shouted Brother Cho.

Qing's expression soured slightly as she looked around for any familiar faces.

Ugh. When I heard that, it turns out it was Brother Cho.

He was the grandson of the Wulin Alliance Leader and the heir of the Black Dragon Clan.

Also, he was a leading figure among the current generation's Rising Stars and was considered a manly and magnanimous free spirit.

But he was also the very same Brother Cho, Cho Hakche, who was known to be crazy about women.

Should Qing greet him or not?

But if it's at Jinhae Pavilion, she really wanted to go.

According to the assessments of martial artists who traveled throughout Wulin, Guangzhou was considered to be a very boring city.

It was said that there were no particularly famous scenic spots around Guangzhou.

This was because historically, Guangzhou was an utterly remote region and was not a city with a long history, since it had only been developed rather recently.

As one could see from the fact that the Han Chinese occupied an overwhelming majority of the population, it meant that the Han people had only immigrated here after Guangdong was developed.

It was a region where the Wokou Pirates frequently pillaged and going out to sea was also prohibited by national law.

As such, while it was the center of Yang Guang and the largest metropolis in the Southern Zhongyuan, if asked if there were anything worth seeing from a tourist perspective, the answer would be… maybe?

One of the only options was one single place, the Jinhae Pavilion.

It was Jinhae Pavilion, the best tavern in Guangzhou.

But when the atmosphere at the Jin Family Estate was not good, she was too afraid to go, and once the atmosphere turned good, she felt it was too awkward to go alone if the Jin family did not offer first.

Even if she went with her own money, it was okay if she was visiting it while they were having this celebration because they had just arrived. However, if she was going to use her own money while residing there for a while, it would be seen in a bad light.

It would look as though the Jin Family was too incompetent to properly serve its guests.

Of course, it wasn't that the Jin Family was treating Qing poorly, but they were just too busy with managing the estate with their small numbers and had no time to spend on their guests.

So, well, even if I wanted to go, what can I do.

But I do have the money, so why can't I go?

I have money to spare and can't visit the city's best bar?

That was when she heard the shouts of joy from the Wulin Alliance combat unit that was heading to Jinhae Pavilion as soon as they had arrived, which made it difficult for her to simply pass by.

But Brother Cho was a bit too burdensome.

It was then.

Among the many faces chattering with their peers, Qing saw a familiar face.

"If it's Jinhae Pavilion, isn't that the best bar in Guangzhou? There are plenty of beauties there as well, right? As expected of a Daoist, you know all the best places to go. You wouldn't be that one, the Sword of Intoxicated Subjugation that cannot drink alcohol without a woman, would you?"

"Of course! After all, the true taste of liquor only comes when a beauty supports it with her slender hands and tips it over with a humble gesture. Today, this Daoist is going to-"

"What's this! Isn't that Changbin!"

At that voice filled with delight, the young martial artists of the support unit turned their heads at once.

Over the sounds of sharp breaths and whispers saying things like "Heavenly Blade," and "Young Lady Ximen," Qing confidently walked over and casually put her hand on Changbin's shoulder.

"Uh, Young Lady Ximen? A-Are you doing well……?"

Changbin's entire body twisted awkwardly like a doll being controlled by a child.

"Wow, you've gotten so awkward after not seeing each other for a while. Just relax, I said, relax."

"U-Uh, that's what I'm d-doing……."

"You don't look like you're relaxing, though?"

"No… I'm relaxed. It's just… h-how have you been?"

"I'm always well, you know."

Qing giggled and poked Changbin's side with her elbow.

'What's with all of you? Didn't the Gyerim Sword Sect already inform you that Young Lady Ximen is staying at the Jin Family Estate? Why are you all acting like such country bumpkins, heh, Sword of Intoxicated Subjugation. You dare act friendly with our Heavenly Blade Young Lady…….'

Cho Hakche gritted his teeth.

At that sound, Qing thought to herself, ‘Oh, he's still the same'.