\chapter{Telepathy (8)}

The other special room guests showered her with countless words of gratitude.

In truth, it wasn't just out of pure gratitude.

Guests in special rooms were usually not ordinary customers, but big spenders who would spend gold sycee just for a day's worth of alcohol.

To such people, connections were the most important treasure in the world.

So, under the pretext of repaying their gratitude, they would offer words of thanks, use that as an excuse to extend invitations, and hopefully they could become friends after a glass or two of alcohol. The best case scenario was that they could become relatives by gathering children and relatives, and if not, it was not a loss either.

And just like that, big spenders who had brought their daughters along were giving their daughters a look.

Their daughters, too, thought that a promising young star in Wulin with an unyielding and handsome aura was a hundred times better than a political marriage with an unknown partner.

It was a moment when the interests of father and daughter aligned.

Using the unique intuition of women, the young girls who had received a life-saving grace quickly found the most approachable people: two clung to Changbin and two to Jo Hakche.

The rest of the promising young stars were a pity, but they should have raised their realms higher if they had felt wronged.

As such, Jo Hakche's mouth was completely agape.

Changbin, on the other hand, was quite troubled.

"Great Expert, Great Expert, please also accept this liquor of mine."

"Mmm."

"Oh my, how taciturn. Indeed, men must prove themselves with action, not words, right?"

"By the way, Great Expert? Do you perhaps have other duties tonight?"

"Cough, Cough."

"Oh my, even the way you spit is so spirited. Ah. Right, now that I think about it, it seems like mice are entering my room lately. If it's not too much trouble, would you be able to help this maiden? T-Tonight?"

"B-But… m-men and women… should be separate… How could…"

Changbin's eyes spun around.

And among all that, one woman was focused on a different target.

"This Lanlang has opened her eyes. The greed of humans is such a terrifying thing. Indeed, it swallows everything."

She then extended her finger and poked Qing's upper abdomen.

"Ah, what the hell?"

"I poked you because I wondered if you would explode. It is quite hard."

Lanlang had slipped in during the victory celebration, roughly after they passed this point.

She had been sitting next to Qing, staring and observing her eating.

Occasionally, she would say "Oh", "Wow", "Amazing" in an emotionless tone, as if she wasn't surprised at all.

"You're gonna get indigestion. Did you come to watch a show? Why are you staring at people eating?"

"To be honest, this is definitely a rare spectacle to see in all the time that Lanlang has existed. Lanlang guarantees it. Please take pride in it, Sky Blossom Sword."

"Agh, please go away."

"Sky Blossom Sword cannot force Lanlang's free will."

"Ugh, seriously. I'm starting to wonder if I need to use physical means."

"Violence is fine, but it is not good for harm to come to Lanlang."

Lanlang said that as she skillfully slid back.

She doesn't seem to be moving her knees that are still on the ground, so does she have wheels underneath or something?

It was then.

Jo Hakche, who was not satisfied with having women on both sides, finally came over to Qing's table, where there were three women, and after seeing Lanlang, he startled.

"T-That beautiful Young Lady? Have we perhaps met somewhere before?"

"Lanlang does not wish to answer."

Qing's face brightened.

Yeah, go on, make your move, make your move.

This was the first time I'm happy to see Jo.

While I'm at it, should I perhaps help Changbin, who seems to be having a difficult time with those aggressive physical assaults?

Wow, look at those girls. They're straight up rubbing their breasts on him.

At this rate, Changbin is going to have breasts on his arm.

Come to think of it, I don't really need to stop Changbin's best moment.

I might as well console my Dragon Flame friends, who look like they're going to gouge their eyes out of jealousy.

That was what Qing thought as she started to get up.

"Ah! Hahou Pyo Mae! It's me, Jo Hakche! Do you not remember?"

"This bastard still has no tact. And yet he doesn't forget a single woman's face. He's an absolutely repulsive, disgusting bastard."

"Eh? Pyo Mae?"

Pyo Mae, to be exact, means a cousin, but in Zhongyuan, cousins are usually not distinguished from siblings.

If it had to be used, it might be for a very distant relative.

"You two know each other?"

"Ah. She is my cousin."

"That is not true. Lanlang does not have such a cousin."

Their opinions differed.

However, neither of them lied.

The Jo and Hahou Clans were basically like sworn brother families.

Qing had only flipped through the Three Kingdoms in the past, but she immediately understood where the Jo and Hahou had become sworn brothers.

That's great.

Why don't I just leave them to reminisce about the good old times and go on my journey to other tables?

That was what Qing thought as she shifted her heavy bottom.

"Lanlang is just Lanlang. The Hahou Clan has been annihilated. Hahou Lanlang is a dead person who no longer exists in this world."

"I… I am sorry to hear that. About your family…"

"It is fine. However, I shall graciously accept your condolences."

At this, Jo Hakche's face became gloomy.

Even if he was a womanizer, he wouldn't lust after a woman in front of his cousin who had lost her entire family.

Qing, who had been shifting around, acted as if she was re-adjusting her position because she felt uncomfortable for some reason.

Ugh, why is the atmosphere suddenly like a funeral?

"It is the truth. Lanlang is no longer hung up on it. The past is the past. Lanlang is only looking forward to the future."

At this, Jo Hakche's expression became even gloomier.

Lanlang tilted her head.

"This is nothing but the truth. Why do you not believe it? Ah. I understand. Is it because Lanlang has no facial expressions? It is because after the annihilation of my clan, my body has become unable to express emotions through my face. But that does not mean I have no emotions at all, so the pervert of the Jo Clan can rest easy."

Although she had no expression, the fact that she referred to him as a ‘pervert of the Jo Clan' already showed that she was not fond of him at all.

Jo Hakche, having read that, smiled bitterly with a much lighter expression.

"Okay. If you ever need help, visit the Jo Clan."

"I need help now. In order to repay this debt of saving my life, Lanlang plans to observe, no, serve the Sky Blossom Sword."

"Eh. I don't need it, wait, Hyu Mae? What's wrong?"

Suddenly, a soft sensation wrapped around Qing's arm.

Qing stopped speaking and turned her head.

For some reason, Gyon Puhee's face, looking desperate, was right in front of her.

Whether that was or wasn't the case, Lanlang continued to speak.

"You do not have to refuse."

"I'm not refusing, I'm saying I don't want to. Who gave you permission to do this-"

"I refuse your rejection. Lanlang's heart cannot be controlled by Sky Blossom Sword. Because Lanlang's heart belongs to Lanlang."

"Ugh, what kind of woman is this."

"That's right. What kind of woman is this."

Gyon Pohee chimed in.

However, Lanlang's expression showed no change whatsoever.

"Very well. As such, Lanlang currently needs a large sum of gold in order to enjoy her only hobby, gourmet cuisine. Jo Brother, please provide Lanlang with material assistance quickly."

"You're still calling me ‘Brother' only when you need something."

"Hurry and give it to me, you pervert of the Jo Clan."

At this, Jo Hakche took out a book of bank notes from his bosom and handed it over as a whole.

"It should be about one hundred sycees."

At that, the two women who had been clinging onto Jo Hakche gasped.

It was a scene where he casually handed over a hundred gold sycees as if it was just an allowance.

Qing looked at him a little differently.

Actually, wouldn't that assessment of him as someone respectable, if not for the women, have come from somewhere?

"Thank you. However, I will not visit the Jo Clan. Lanlang will continue to be reminded of unpleasant memories from her past connections."

"Okay. That's understandable. Then, I should probably disappear for a bit. Young Ladies, how about we go have an intimate conversation in a quiet place?"

"Yes!"

"I would love to!"

The two women's eyes lit up.

"Perhaps Young Lady Ximen would also-"

"Do you want get hit with pig's trotter too?"

Never mind, huh.

I just hope I don't see you again.

Even while disappearing with the two women, Qing threw a handful of well-oiled pig's feet at the back of Jo's head, who was still talking about a next opportunity.

The pig's feet, having drawn a parabola, stuck into Jo's hair.

As Jo left as one with the pig's feet while receiving envious glances, Lanlang remained, having gotten a bit closer.

"Are you curious about Lanlang's past? It is not a special tale. The Hahou Clan was annihilated for treason."

"Ah."

It's you again, Emperor? Why is the state of the country like this?

As Qing's expression crumpled, Lanlang shook her head.

"There is no need to pity me. It was because they were actually preparing treason."

"Ah. Really. I see."

"The Hahou Clan was annihilated because they lacked the strength. If they hadn't, the royal family would have suffered. That's all there is to it. Lanlang does not hold resentment about this matter."

"Ah. Okay."

Hmm. I have no idea what to say.

At that, Lanlang spoke again.

"However, if you are willing to provide this Lanlang with emotional support, I shall let you know that Sky Blossom Sword's unrefined, unclean, and disgusting eating habits have given this Lanlang unprecedented joy. To think that a human eating could provide such enjoyment. Lanlang's eyes have been opened to a new world."

"Please, I'm begging you, can you please just go away?"

"I am sorry. Lanlang does not wish to grant your request. I am sorry. I lied. I am not sorry at all."

"Ugh, please, just go away."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Not long ago, there was an old man who embarked on a long and winding journey, crossing mountains and rivers.

Since it was a kind of flight, it was not an easy journey for his old body as he hurried.

But the old man had dependable children and cold beasts he was raising like his own, so he was not lonely.

An old man who raised several venomous snakes in his bosom, people of Jianghu called the old man Sa-Sa's Boyeol.

Also, he had a new disciple.

Although he was dull and could only understand one thing even after teaching ten, he was obedient, as he had not been chosen for his talent from the start.

And thus, he finally reached Hubie Province and Zigui County!

As the manor of Seol's Trading Company came into view from afar, Boyeol's heart became complicated.

They said it was a small trading company, but it's really small.

No, why introduce me to a genuinely small trading company? The old hag didn't trick me again, did she?

For now, That child had recommended it, so I came here, but the manor of the trading company was far too small.

At this rate, it would be impossible for this to become a base.

Of course, just by staying in Hubei, it would become difficult for the Unorthodox Alliance to do anything.

What could those of the Unorthodox Faction possibly do in Orthodox territory? The problem was the members of the Orthodox Faction.

Could this small trading company become a safe haven from the grudges with the Orthodox Faction?

But it was Boyeol who was desperate.

Even if it didn't work out, if he mentioned the name of Sky Blossom Sword, he would at least get a few pennies. Even if I couldn't eat it myself, I'd have to feed my babies (snakes) some nourishing food.

He had forgotten about the harsh winter weather of Zhongyuan after only staying in Guangxi for a short time. After all, wasn't the cold weather a natural enemy of snakes?

And so, after having his disciple rest at an inn, he approached Seol's Trading Company.

But wait?

Something's…

Something isn't right.

The people with carts, those carrying loads, and even the women pushing vegetable carts were all glancing over here.

And they weren't glancing secretly.

It was more of a warning that they were openly watching him.

Even the errand runners coming and going from Seol's Trading Company were mostly Peak Realm Masters, not even hiding their presence, and there was also the occasional Transcendent Realm Master, along with a few First Rate ones mixed in.

This was no ordinary trading company.

Sa-Sa's Boyeol swallowed nervously.

As he reached the front gates of Seol's Trading Company, he saw that even the gatekeepers were masters of the Peak Realm.

"Greetings. Honored Senior, what is the purpose of your visit to this trading company?"

Sa-Sa's Boyeol cautiously took a shot.

"Is this Seol's Trading Company? I am a physician named Sa-Sa's Boyeol. I have a connection with a child named Sky Blossom Sword, or rather, Ximen Qing, and she recommended me, saying that I might be able to help with the work."

Then, the gatekeeper's demeanor suddenly changed.

In a good way.

The gatekeeper's face broke into a bright smile.

"Ah, did the Young Lady recommend you? You should have said so sooner. Please come inside. Ah, this winter is particularly harsh, isn't it? May I ask if you enjoy warm tea or alcohol?"

"Uh, I enjoy tea."

"Ah. Fortunately, we just acquired a fine old tea. Please allow me to guide you to the Trading Company's Main Room."

Old tea, also known as ‘Laoqing', was a specialty of Hubei, and the tea that represented Hubei Province.

And as was the usual case with the teas that represented a region, it was incredibly expensive.

A tea fanatic, Sa-Sa's Boyeol's mouth watered and a smile reflexively spread across his face.

Then…

"Hey, did you hear that? He's Young Lady's guest! Everyone, disperse!"

At that moment, countless people who had been walking past the trading company suddenly scattered in all different directions.

And what was even creepier was that all of them were grinning.

Sa-Sa's Boyeol's heart skipped a beat.

The Masters disguised as workers were just a smokescreen; the main forces were those passing by, disguised as ordinary people, their blades sharpened and ready.

Boyeol became nervous about something else.

What, what in the world is this?

Why in the world did Sky Blossom Sword establish such a force in the territory of the Orthodox Faction, and even right in front of her own sect, the Divine Maiden Sect?