\chapter{Telepathy (6)}

Yi Wangchul's mind raced.

The Strategist Fang was already done for.

The details of his twisted arm were that he would live as a cripple, a serious condition, but a cripple was only possible if he survived.

Rather, the gash on his neck was proof that the bloodthirsty fiend, who was clearly proficient at killing people, was aiming to kill him for sure.

How could one deal with bleeding from the neck in the first place?

If one tried to stop the bleeding by strangling the neck?

They would kill the person before they could stop the bleeding.

Therefore, Yi Wangchul's concern was not how to save Strategist Fang.

"Damn it, the strategist lent by the Sado Alliance."

The problem was the Sado Alliance.

They had lent one of their top strategists, but instead of treating him well, they couldn't even look after him properly, resulting in his death. (He wasn't dead yet)

How could they possibly explain this?

Even if they said they found Strategist Fang dead on his way to the latrine, it would be absolutely no excuse.

They'd only incite the Sado Alliance's rage by asking: "Did you leave such a frail strategist go to the latrine alone?! You, a small-time gang, should have at least set up silk carpets to the latrine so as not to sully him with even a bit of dust! And are you trying to call that an excuse?!"

What person in the world would want to be escorted and attended to even on their way to the latrine? But this was the sorrow of a minor gang.

So there was only one way to avoid that wrath.

Revenge!

At the very least, he had to find that fiend and take thorough revenge, then loudly proclaim to the world, "This is what happens when you touch a member of the Sado Alliance!" in order to give the Sado Alliance some justification for looking over their mistake.

Flames of rage flickered in Yi Wangchul's eyes.

Of course, this wasn't because of the grudge of having his beloved, or rather used-to-be-used, Strategist Fang killed.

Yi Wangchul was also a member of an Unorthodox sect, and hating scholars was a fundamental trait among them.

He didn't like Strategist Fang, who was just barely a Third-Rate martial artist but was too proud of himself, and so Strategist Fang, who had been killed, was nothing more than a useless, dumbass idiot.

Yi Wangchul's anger was purely because of the damage he had suffered.

Damn it, this way, I can't even ask the Sado Alliance for help again.

If we could get just one more chest of elixirs, we could become a large gang that could exert influence beyond the prefecture, but now…

All because of this useless moron and that fiend.

"Find out who that bastard is. Even if they don't exist, find them."

The phrase, "Even if they don't exist, find them," wasn't a statement of grit to find whoever it was.

It meant that if there was no one, then just make one up.

At this, the Salwol Gang warriors simultaneously threw open the paper doors of the room.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

This was the viewing platform railing located outside the guest rooms of the Jinhae Pavilion.

Therefore, the remaining ‘sister' could showcase such magical skills of opening the door of the opposite corridor while claiming to be just ‘getting some fresh air'.

"What the. Why did you come out from there?"

At that, Gyeon Pohee smiled shyly and then whispered sweetly, her lips close to Qing's ear.

"I went to pee."

Hm. That was information I really didn't want to know.

And why did she have to say that now, of all times, while I'm happily slurping on the Nourishing Elixir Tea? Ah well, it did taste good, though.

But it was understandable for Hee-mae to do that.

After all, she was Hee-mae.

In truth, Qing wasn't a refined type of person who would be disgusted by such a minor thing anyway.

Qing even chuckled and asked back.

"So? Was it refreshing?"

"Yeah."

"How was it there? Was it clean?"

"Yeah. It seems like it's a good inn."

That was good news to hear.

Clean bathrooms were a rare thing, after all.

She should also go there later, she thought.

That was when it happened.

They heard a loud crashing and breaking sound from outside.

Someone was shouting, and someone else was shrieking at the top of their lungs.

At that, the members of the Crimson Dragon Squad all stopped moving and closed their mouths as if they had rehearsed it.

Cho Hakche, who had been glaring at Changbin with bloodshot eyes, was now composed and was tapping on the table, as if nothing had happened.

At that, the young men who had been sitting at the main table outside opened the paper door towards the railing, letting the night air in.

And at the same time, a thick fog of alcohol rose up.

The members of the Crimson Dragon Squad simultaneously dispelled the alcohol in the air, creating a thick fog of alcoholic mist.

It wouldn't linger for long, since the paper doors were left open. It soon melted into the night air.

Oh. That was pretty impressive.

Qing marveled.

This was the power of the Orthodox Faction… No, rather, it was due to the fact that it was a drinking party that had two plus one ultra-beauties of the Wulin and three more people.

If it had been just men, or if they were entertaining the company of courtesans, they wouldn't have been able to go into battle preparations so neatly and immediately.

So in a way, it was thanks to Qing's thoughtless intrusion.

Or rather, it was due to her ravenous gluttony that couldn't help but put her face to any food or alcohol, that was a victory born from that.

Meanwhile, the crashing, shrieking, and screaming sounds were gradually getting closer, and finally, bang! The paper door broke away from its frame and fell to the floor.

Ignoring the sideways sliding door etiquette of Zhongyuan and forcibly pushing the door forward, a Salwol Gang warrior appeared with a sword in hand, shouting proudly.

"Kneel! You bastards…… Oh?"

They had made a grand entrance to intimidate them, but…

The Salwol Gang warrior trailed off when he saw about thirty weapons aimed at him.

Thirty members of the Crimson Dragon Squad. And three more to top it off.

Countless requests for handshakes from swords and Sword Qis.

The Salwol Gang warrior, using the secret technique of the Sado Alliance, retreated as naturally as if time was flowing backward, as if it had never happened—

Swish. A terrifying sound that brushed past his ear.

He didn't even see what had passed by.

The Salwol Gang warrior stopped abruptly.

Then, with a somber expression, he opened his mouth.

"Should I kneel?"

Cho Hakche nodded solemnly.

The Salwol Gang warrior knelt down and placed his dao on the ground.

Everyone here, at least two people excluded, were righteous experts of the Orthodox Faction.

That meant at least two people wouldn't try to cut down and kill a defenseless opponent who had lost their will and chose to be neutralized.

Cho Hakche spoke calmly with a much more relaxed demeanor.

Cho Hakche might have his eyes go crazy whenever he saw women, but his true nature was that of a big, great guy who was praised by all the young people of the Orthodox Faction.

Though to all the young people (women) of the Orthodox Faction, he was, without a doubt, the person they hated the most, the person they were most burdened by, and the person they didn't want to encounter the most.

"Look here, what kind of outrageous ruckus is this in a tavern used by many people? Of course, if a person is angry, moreover, if they are drunk, then of cour-"

"Aaaah! Those are them! Those are the bastards!"

A shout cut off Cho Hakche's words of gentle persuasion.

And then, a stampede of footsteps rushed in.

In an instant, the paper door was shattered and fell to the floor as the Salwol Gang warriors, with daos in hand, formed a line of defense.

And finally, the Sect Leader made his appearance!

Yi Wangchul entered in a haughty manner, putting on the airs of a Master.

It wasn't because he was truly composed, but because he thought he had to make an entrance like this for it to look good.

In reality, it was a useful piece of life wisdom to intimidate opponents, making them think he was someone not to be trifled with.

As such, while showing off his composure, Yi Wangchul's eyes were caught by a beauty beyond his wildest imagination… no, rather, by a slightly plain-looking beauty (because being next to a stone made it look all the more rough) next to her.

That was Jinseol. Why was she here?

If Jinseol wasn't there, he would have just thought they were some greenhorn punks with swords, but now that Jinseol was present, he knew they were not just mere punks.

"Ahem, ahem. I am Yi Wangchul, the Sect Leader of the Salwol Gang. It seems there was some misunderstanding. My subordinates were in a rage because they were searching for the fiend who so brutally murdered a strategist of the Sado Alliance. That must be why we ended up being rude."

The Sect Leader's choice was a quick retreat.

Although it was a bit unseemly, what could be done?

After all, they were clearly outnumbered, and if they touched the wrong nerve, the Sado Alliance wouldn't be their only issue, so as the leader of the gang, it was a judgment that was worthy of praise.

Cho Hakche paused to think.

Salwol Gang, they were clearly members of an Unorthodox Sect.

Although they had a numerical advantage, the older ones were on the other side, so as a squad leader who was responsible for his members, he could not recklessly start a brawl.

Besides, the Crimson Dragon Squad was formed as a reserve combat unit for young disciples, both to gain experience in Jianghu and expand their social network.

I should have brought the senior members of the Blood Alliance Squad.

As such, he had no choice but to play along.

"A fiend who murdered a strategist of the Sado Alliance? What are you talking about? How could such an unfortunate, no, such a tragic incident happen all of a sudden in the dead of night?"

Yi Wangchul's eyebrow twitched slightly.

A brat, no matter if we are from the Orthodox or Unorthodox Faction, should know I am much more senior. How dare he use the ‘hao' ending when addressing me?

But he understood the signal to try to make the best of this.

From the start, the fact that he was asking what had happened was a signal that they had come to the wrong place, and that it was not their business, so they should quietly get lost without stirring trouble.

Therefore, he couldn't recklessly pick a fight just because the Anti-Communist Brigade was displeased.

"Ahem, a strategist of the Sado Alliance was found dead while taking a breather during the banquet. Since blood was still flowing from the body, I judged that the fiend could not have gone too far and launched a search. But while doing so, we inadvertently ruined the mood."

"Ah. Is that so? Hmm."

That was when it happened.

Suddenly, Qing cut in and raised her voice.

"You can't re-glue a broken mood, can you? If you feel so sorry about it, then pay for the alcohol instead, you know? What's the point of just apologizing?"

At that, smiles slowly spread across the faces of the Crimson Dragon Squad members.

If they managed to get free drinks from a bunch of Unorthodox Sect bastards, that would make for a truly legendary tale to tell, one that would spread far and wide.

On the other hand, Yi Wangchul's face twisted.

What the hell was this brazen young girl trying to do, ruining his face like that?

However, in battles between the Orthodox and Unorthodox Factions, even the smallest of disputes could become a serious showdown.

Yi Wangchul realized that he had spoken carelessly.

He had spoken as if he was in the wrong, and she had immediately hammered in that point by saying ‘sorry'.

What to do now?

If he bought them alcohol, he would be seen as a fool who was intimidated by a young brat and handed over gold and silver.

If he retreated and said he wouldn't pay, he would become a cheapskate who couldn't even afford a single cup of alcohol.

If he claimed that he never said that and that he wasn't sorry?

Then that would simply be an insult. And as soon as he did, he would be giving them an excuse to attack.

It was truly a dilemma!

Of course, Qing was more serious than anyone in the world at making villains suffer, and even showed a burst of intelligence during such moments.

But right now, she was simply looking for a way to swing her sword once.

She had taken down two of them and there was only one left, right?

If she could break the head of this Sect Leader bastard, the rest would be just a disorganized rabble. At that point, she'd just clean them all up and leave with a lighter heart.

But the members of the Crimson Dragon Squad, unaware of this, were inwardly admiring Qing tenfold. They thought they had found one of the biggest and best stories to tell everyone after they finished this mission.

They all thought, ‘The Heavenly Flower Sword is not only beautiful, but so witty as well!'

But it was all a huge misunderstanding and utter nonsense.

It was then.

"Uh. That person. That's that person from earlier."

Gyeon Pohee pointed at the body of Strategist Fang being carried out behind Yi Wangchul.

"Hee-mae? What do you mean that person?"

"Because he kept offering me drinks, kissing me, and trying to grab my wrist, wanting to do ‘things men and women do'. So I beat him up."

At that, everyone fell silent.

Ah. So Hee-mae was the one.

Hmm. Hee-mae can do that, after all. She is Hee-mae.

Ah…… It was on our side, after all.

Damn, it was really those guys.

That same thought ran through everyone's mind.

In that instant, Qing struck first.

"How dare you! Trying to harass this Heavenly Flower Sword's sworn sister! You bastards with eyes that went crazy at Hee-mae's beauty tried to harass my Hee-mae and drag her away to do all kinds of outrageous things! Unforgivable!"

"Wh-"

"No need for words!"

Bang! For some reason, black dust rose up and Qing's figure stretched out like a long line.

The moment Yi Wangchul was startled and raised his dao,

Deeeeeeng-!! A grand, yet not noisy, solemn sound of a great bell rang out.

Heavenly Flower Sword was the Buddha's Palm, and Buddha's Palm was Shaolin, and Shaolin was Master Wunue.

And since the title ‘Heavenly Flower Sword' was given by Master Wunue, if one were to forcibly string things together, it would still make some sense, albeit a bit rough.

Yi Wangchul abruptly recalled the legendary Divine Art that he had forgotten due to such vulgar jokes such as the Three-Headed, One Armed or Five-Headed, Two Armed, and One-Legged Freaks.

However, it was too late. The imposing Buddha's Palm containing an unbelievable force slammed into the ground at Yi Wangchul's feet. CRUNCH!

Martial arts begin at the feet.

Conversely, it also meant that if the ground beneath their feet crumbled, martial arts could not begin.

And by then, the figure of the Heavenly Flower Sword had already struck, reaching before his very eyes.

The Heavenly Flower Sword's hand was raised high.

In that pure, white jade-like, dazzling beautiful hand, was a weapon. On the pig's trotter, a sunset-colored Sword Force lingered.

Yi Wangchul's eyes widened.

A pig's trotter?!

I can't die by getting hit by a pig's trotter!