\chapter{Telepathy (10)}

Except for the fact that his nature was as fiery as a Buddhist, being dragged around by the stubborn Weollyang wasn't actually all that damaging.

It was things like diligently focusing on external training with stances before meals after waking up.

Or diligently focusing on external training even after meals.

And then even going to work together, and then after coming back from work, more external, then even MORE external training.

If asked why he only trained his body all day, Weollyang would say this.

Internal cultivation should be done while others slept, so focusing on external cultivation all day was not a problem.

And that external cultivation was the power that steadily increased the body's inherent strength.

Those who only swung their swords only trained the parts they used. So if they did not achieve enlightenment through that, they would only have an unbalanced body and nothing else would remain.

But if one trained the entire body with external cultivation, even if they did not reach enlightenment, the power that was placed into the weapon would become stronger through the strength of the robust body. Moreover, the workings of the body was the workings of the universe. Therefore, the path of understanding the body was also a path to enlightenment, so he simply couldn't understand why everyone neglected external cultivation.

This was what Qing had asked, and what she had personally heard.

And she had to pay the price for asking.

"Right, you should do it too while you're at it. Originally, external cultivation is more necessary for female martial artists, but they all avoid it, saying it would ruin their forms or build muscle while spouting all sorts of nonsense. But what's more important for a martial artist than their body? And talking about muscle is also ridiculous. As if just basic strength training would suddenly make your muscles bulge like a monstrosity. Now, prepare yourself."

After being dragged to the training grounds, Jo Hakchae, who was drenched in sweat with his upper body bare, sent Qing a desperate look.

'Young Lady Ximen? Did you come to save me?'

'No, I just happened to come here because I was bored.'

If one were to only consider the pure physical ability, Qing's body was already that of the Greatest Under Heaven and the Greatest of All Time.

"Ooh, did you do some external training? This is quite impressive, isn't it?"

"Of course. My Master always emphasizes the importance of external cultivation."

"Indeed! The Godmother is absolutely flawless!"

At that, Weollyang exclaimed in admiration and kept adding more and more weight, making the sandbags one pair, two pairs, three pairs, four pairs, transforming Qing into a sandbag rack where only her pretty face could be seen.

However, she showed absolutely no signs of fatigue, not even sweating a single drop. In fact, she was so bored that she was caught yawning.

Weollyang burst out laughing.

"Indeed! How splendid! To have such a strong body, you are truly worthy of being the successor of the Buddha's Palm! You have inherited the spirit of Shaolin!"

"Hehe. Isn't it said that all the skills of the world originated from Shaolin?"

"Magnificent! Magnificent! I was embarrassed to have said unnecessary things to a giant who had already reached a realm through external cultivation. What I thought was just an adorable child was indeed a true genius and a treasure of the Orthodox Faction!"

"Hehe. It's nothing."

Qing, who had effortlessly acquired external cultivation, received praises.

However, Weollyang was sincerely impressed.

Female martial artists originally hated external cultivation.

They worried about their muscles becoming bulky and even if they didn't become bulky, they didn't want to lose the plumpness of their skin, thus revealing the hardness of their muscles beneath.

He thought she was a genius who had reached the Transcendent Realm at such a young age, but it seemed that she also possessed the sweat and tears of effort from hard and strenuous physical training.

Due to his ridiculous misunderstanding, his evaluation of Qing rose vertically.

Weollyang took off the black knot bracelet he was wearing on his wrist and handed it to Qing.

"Right, take this. It's from the Vajra Strength Association, where we train external strength together in the Alliance. If you ever visit Kaifeng later, let us sweat together. The black color indicates the teacher level, but from what I've seen, you are more than qualified to be a teacher."

"Ah. Okay."

She took it because he gave it to her.

Qing inadvertently found herself gazing at Weollyang's shiny, bald head.

What is it? Is he a monk because he's bald and not the other way around? Did he put oil on it or something? It's so shiny.

For some reason, the name Vajra Strength Association made her imagine a scene of bald muscle monstrosities, sweating and working out in a foggy, strange place.

Noticing the disrespectful gaze, Weollyang smiled and added.

"There are plenty of people your age there too, so don't feel pressured to visit."

"There are people my age there?"

"Of course. For starters, there's Yi Hyeon, the guy who broke the record for the youngest teacher. And also…"

Starting with the name of Jegal Yi Hyeon, the list of young members of the Vajra Strength Association went on endlessly.

In fact, the smaller and weaker the sect, the more keenly they felt the importance of external cultivation, and as such, they also knew the importance of connections.

So the Vajra Strength Association, where one could gain both external cultivation and connections by just training, was originally far more popular.

But the person at the very front of the list just had to be Jegal Yi Hyeon.

Although Jegal Yi had plenty of hair, she still couldn't shake the image of a strange scene filled with muscle monsters and sweat-fog.

Qing stared at the Vajra Strength Association knot bracelet.

It was a bit damp somehow, so she should wash it first.

But still, it was a symbol of a group.

It seemed good to have a sense of belonging. Should I make a "HalfSword Double Daoist Association" or something?

As such, they had a body-limit testing session disguised as external cultivation, but they failed to measure anything because there weren't enough sandbags.

"Young Lady Ximen? Could you spare me some time?"

It seemed that Weollyang's theory that ‘if the body is exhausted, the lustful desires of women will disappear', had some effect, as the lecherous look in Jo Hakchae's eyes had subsided.

Still, Jo Hyung was a bit much.

Even if the woman tempted him, how could he just abandon his unit and go have fun, acting so self-righteous?

Qing's hearing was not ordinary.

She could hear the strange sounds from downstairs. For example, "Behold! This is the black dragon ascending of the Black Dragon Gang, the hegemon of Heilongjiang," or something like that.

As such, she had listened without thinking and kept on listening when she heard that, "The Great One's black dragon is… Ah, haah, haah." The sounds were so ridiculous that she couldn't help but laugh. Ah, it's funny again.

To give birth to the Black Dragon's child. No, wait, what the-

Let it ascend! Let it ascend while riding a dragon. Hehe.

"Puhah."

She ended up bursting into laughter.

Whether the women were simply going along with Jo Hyung's narcissism, or were truly impressed by a thing that could be called a black dragon, she didn't know.

How would one know if it was a black dragon or a black worm?

"Young Lady Ximen?"

Qing forced herself to stop laughing and answered.

"Ah, no, it's nothing. Jo Hyung, just asking made me think I'm going to become extremely busy. What is it you wanted to talk about?"

"That, uh, about the Ha Hu girl."

"You mean Young Lady Rangrang2?"

At that, a shadow passed over Jo Hakchae's face.

"Please take care of her well. Since her family was destroyed, the emotional wounds she must have incurred should be quite great. She must have been so shocked that even her speech became so strange."

"Eh? Wasn't she always like that?"

"Of course not? It seems she had a huge shock to her head, or, uh, something like that."

He was basically saying that she had gone crazy.

Qing also had a similar feeling.

"But still, she is a very kind Young Lady. In my life, I have never seen another child as kind as her. She is the type to never turn a blind eye to others' suffering, to the extent that there is no one in Jilin who has not received help from her. Because she had used half of the Ha Hu family assets to do relief work."

She was a fool who only gave without ever taking.

It was said that there were no usurers in Jilin because she had given help so generously.

Originally, usury was the last choice made with tears in one's eyes when commoners' lives became difficult.

Commoners weren't idiots, after all, and it wasn't like they willingly used usury with high interest rates where they were devoured bit by bit with all sorts of excuses.

Conversely, if their lives were not difficult, there would be no reason to use usury.

When she saw orphans, she built them homes and fed them. When she saw the sick, she called physicians and provided them with everything from house calls to treatment and medicine.

It was fortunate that there were no bad harvests, or else the Ha Hu Family would have gone bankrupt while feeding all the commoners.

"It's just that, at times, she seems like a complete idiot. Hmm."

"Hmm. I see……"

Qing's response lacked any strength.

For someone like that, her Righteous Karma should be easily over three digits. But where did all the Righteous Karma go? All that was left was just a single point.

It didn't seem like Jo Hyung was lying, but since it was a story about a relative, it was a basic trait of the people of Zhongyuan to throw a fit and say they had seen a serpent when they had only seen a slightly bigger worm.

Hmm. Black dragon. Black serpent. Black worm. Whatever.

"Hey, Jo! It's time for dinner!"

At that, Jo Hakchae's expression turned desperate.

"Young Lady Ximen. Perhaps, could you grant me, this Jo Hakchae, the opportunity to treat you to dinner?"

"Ehh, if Weollyang Master calls for you, who am I to steal a Young Master from him? Ah, he must be waiting."

Qing said that and turned around immediately.

"Young Lady, Young Lady Ximen……!"

Jo Hakchae called out to Qing with a desperate voice, but it was his own doing, and he had to live with the consequences of his own actions.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The fight at the Jinhai Pavilion was, in fact, wrong.

It was a vile and cruel maneuver that ambushed and killed the head of a sect, as well as destroying his body and honor using a pig's trotter.

But in truth, if he were to be honest with himself, Jin Clan Lord also found the result to be praiseworthy.

Just how much was he indebted to that child, the Heavenly Flower Sword? She was such a benefactor to the clan that it wouldn't be enough to give her everything they had.

At any rate, Jin Clan Lord was planning to eradicate the Unorthodox Faction of Guangzhou with this opportunity.

Of course, an event of the Orthodox Faction was different from those of the Unorthodox Faction. They couldn't do whatever they wanted without any regard for the time, place, or the situation of their opponents like the bastards of the Unorthodox Faction (plus Ximen Qing). The Orthodox Faction had to show their righteousness.

As such, he was planning to wait quietly until the sect leader's funeral was over.

Once the funeral was over, the Blood Moon Sect would receive their final notice.

Those who did not leave would be subjected to the laws of Wulin.

Hmm. If I were to tell them to leave within a week, one week was too long.

It seemed like the Unorthodox Alliance would be able to send reinforcements if they had that much time.

But three days was too short.

Was it four days or five days? That was the question.

While the Jin Clan Lord was pondering over the deadline of the final notice, Wang Woo, the new big brother of the Blood Moon Sect, was also pondering for the exact same reason.

How much time would those Jin bastards give them?

Since they were from the Orthodox Faction, would they give them a week?

If the Snitch cried and whined properly, maybe reinforcements could come within a week?

Or should he just go there and beg for forgiveness on his knees right away?

The Orthodox Faction wouldn't use force to destroy them if they publicly apologized in front of so many people.

It was not because the Orthodox Faction had kind hearts.

It was because they were bound by things like honor, righteousness, and dignity that they had created for themselves.

But if they apologized like that, they would usually try to receive something in return such as the lives of the leader and a number of the top-ranking members, or the retirement of a warrior who had their dantian broken or their arms cut off.

If I die or become crippled, there's no point in the Blood Moon Sect remaining.

As such, Wang Woo had no choice but to continue pondering.

And so, on the third day after the death of the former Blood Moon Sect Leader, Lee Wangchul, and the second night of the funeral, deep into the night……

In the Small Dragon Hall of the Blood Moon Sect Estate.

It was the accommodation for the newly initiated third-generation disciples, or, as they were called in the Blood Moon Sect, the hope for their future.

They were the sect's dream trees who had their realms dramatically increased by eating elixirs thanks to the Unorthodox Alliance.

However, they could not sleep due to a strangely terrible thirst.

The day they were to complete their training by eating the final elixirs, prepared by the Chief Strategist, was today.

But those elixirs had been replaced with the Inner Qi of the Blood Moon Sect leaders.

Their throats were parched.

A scorching thirst.

No matter how much they drank water, alcohol, or any other liquid until their stomachs burst, the terrible thirst would not subside.