\chapter{Telepathy (3)}

"Young Master Jo. Are you also doing well?"

At that, Jo Hakche looks up with a menacing glare.

Men always think that when they erase their smiles and glare with a scary look, they look cool, all based on instincts they can't understand themselves.

But that is nothing but an assumption stemming from male instincts, and in reality, it does not look cool at all.

"It has been a long time. Ah. By any chance, are you free this evening? I'm planning to visit Jinhaeru with my close brothers, and I was hoping that the beautiful Cheonhwa Sword would join us and grace the occasion with her presence."

His voice was lowered as much as possible.

That, too, was something men thought was a cool mannerism.

However, to be clear, rather than a high-pitched voice, a low-pitched one was much better.

After all, if one's voice was thin and high-pitched, one would sound like a eunuch or a castrated official.

"Oh. Really? Are you going to treat, Young Master Jo?"

"Haha, of course! This Jo Hakche! Will serve you properly tonight!"

Hmm. ‘Serve properly'? What's that supposed to mean?

Is he in the hospitality business? Or is that a way of speaking like the men from Busan, as if saying ‘I'll treat you to the best possible hospitality when you come to visit' when they go out to have fun?

At his words, the members of the Hwaryong Group began to murmur.

"Uh, Leader Jo? Isn't it supposed to be a genuine show of brotherhood between men?"

"What was that? Are we supposed to go hang out with those dirty men and stink of sweat?"

"No, that…"

The faces of the Hwaryong Group members looked disheartened, with a hint of disappointment.

At that, Qing realized something.

Now that I think about it, I might be an inconvenience if I go.

A gathering for a genuine show of brotherhood between men was completely different from one where the Cheonhwa Sword was present, all eating and drinking together.

To the members of the mid-small sized factions, the Cheonhwa Sword was someone who stood atop a distant, faraway cliff.

They couldn't compete with her in terms of status or martial prowess, and her beauty, which surpassed a certain limit, only made them feel astonished, thus losing even the will to try and forge a relationship with her.

"Ah! Ahh. You were intending to go that way. Everyone is. Look at me. It seems I was so tactless. Well, it's a rare occasion so you should have fun and get some rest. Hmm? In a manly way?"

I was assuming you guys were going to have a fun time with the gisaengs, doing healthy, wholesome things, but it seems I was tactless.

Go and have fun, then.

There were times when consideration could be more miserable.

It was a somewhat bitter thing to say to a woman.

Instead, Qing changed targets.

"Ah. Changbin, do you want to go too?"

"Ah, that, no, it's not that. Since we are gathering together as a group, it's not like I want to go to play or anything. Absolutely not."

"Oh, really? Then will you eat with me? They say alcohol tastes better when served by a woman, right? And I am a master at pouring alcohol. Let me tell you, you will never have an empty glass tonight."

"Uh, just the two of us? That's kind of…"

"Guh, Changbin, you're doomed……"

There was a background sound as if someone was grinding their teeth, but Qing ignored it as if she hadn't heard it.

However, Changbin was hesitant and did not seem interested.

"What's wrong? Why?"

"T-The two of us, it's kind of, well, you know, men and women should be distinct."

"Hey, there's no distinction among friends."

However, Qing had no intention of yielding.

Changbin's vision went dark!

Just the two of us? This won't do! It'll be awkward for sure! What should I talk about? I had some stories in my mind before, but why can't I remember them……?

"And it won't be just two of us, you know? When I was eating that bean curd snack a while ago, I spilled some stuff on my clothes, so I went to clean up. Oh, look, here she comes. My Sister in Spirit!"

When Qing waved her hand, calling for Sister in Spirit, the heads of the Hwaryong Group members turned at once-

And then they all gasped, as if singing in harmony.

Could this have been how Daji, the peerless bewitching woman who had the Shang Dynasty under her thumb during the Shang-Yin Era, was like?

She was the very definition of human lechery, a genius at making men fall for her, Daji reborn, the bewitching woman under the heavens.

With just her appearance alone, the bewitching woman gripped the people present as she suddenly opened her red lips, revealing her white teeth and smiling mischievously as if she was a beast who had discovered its prey, ready to capture and devour it in another way.

That was how it looked to others, but for Qing, it was merely an expression of peak joy.

"This is my Sister in Spirit, my Sister Jieh, Gyeon Pohui."

For reference, the character jie (姐), meaning elder sister, was a character that wasn't used very commonly in Zhongyuan. This was because the character had a narrow meaning of only referring to elder sisters born from the same parents.

Since it was common to have multiple wives and concubines in Zhongyuan, it was a character that could not be used even if they only had different mothers, so they just used jie (姐).

That was the same jie in Senior Sister and Junior Sister.

"Come to think of it, haven't you two seen each other before?"

"No? This is my first time?"

"Ah, was that Hyun then?"

"Hyun? Who's that again?"

"You know, the one who's really tall and has muscles. Like that. All huge and buff."

"Ah. That younger brother who talks too much."

"Ah. It was Hyun then. Anyway. This is my friend, Changbin. A Plum Blossom Swordsman of the Mount Hua Sect."

"Nice to meet you. I'm Gyeon Pohui."

It was Gyeon Pohui, who spoke informally from the very start.

There was no particular reason for it, perhaps just because he was a friend of her younger sister?

However, Changbin's vision went dark yet again!

"Y-Young Lady Ximen, are you perhaps, going to be dining as a trio with us……"

"Yep. Yippie, Changbin, aren't you lucky? A flower on both arms."

Addeudeuk, you bastard Changbin, I'm going to kill you, I'm going to kill you with curses…….

Once again, a background sound was heard, but Qing ignored it as if she didn't hear anything.

"Yippie, Changbin, you got so lucky today, you're on a roll."

The effect was amazing!

Changbin's consciousness was fading away!

Just being with Qing alone was already making him feel as if he was about to suffocate because of the awkwardness, but now there was an unknown woman joining them.

Changbin frantically tried to use his brain.

"Th, th! Th…"

"Yeah? What is it?"

"That's right! Young Lady Jin! If this is the case, we should also invite Young Lady Jin to join us……."

"Ah! I didn't think of that. Yeah, that's right. It wouldn't do for us to go without her, right? Wow, Changbin, not two but three, huh? Wow, the Flower Boy, a man of magical appeal."

Changbin sighed in relief, although he was sweating profusely.

At least it wouldn't be just one man with three women. Then he would just silently drink and not talk.

"You, Changbin, you really should have them all to yourself. Is that the only way you can feel satisfied?! I will never, I will never forgive you."

It was the form of Cho Hakche who looked like a dense fan of pitch-black hatred was spreading out.

Qing figured she couldn't ignore him anymore.

"Ah. Young Master Jo, you're still here. This is my Sister in Spirit, Gyeon Pohui. Sister, this is Young Master Jo Hakche, and, well, just someone I know?"

The words, ‘just someone I know', pierced straight into Jo Hakche's heart.

"Guh."

"Ah. You're just someone I know. Hmm, Sister in Spirit? How do I greet someone I just know? Should I just say it's nice to meet you?"

"Kuhheueuk."

Jo Hakche clutched his chest.

At that, Gyeon Pohui tilted her head.

"Are you feeling sick anywhere?"

"No, it's just that when I saw Young Lady Gyeon's beauty, my heart was racing intensely. It was like an unstoppable pulsation. Do you perhaps understand what this feeling is?"

A booing sound came from the side, as it was such a cheesy comment that didn't warrant high marks.

At that, Gyeon Pohui tilted her head again.

"Ah. You have a bad heart, huh. Oh my. How can a martial artist have such a weak heart? Please, take care. What did you say? Someone who knows my Sister in Spirit?"

"Kuhh, I will never forgive you, Changbin! Never……..!"

"No, why me, though?"

Regardless of that, in the end, it was decided that the Hwaryong Group would all go to Jinhaeru together.

The situation had become awkward to even separate into smaller groups and have them play separately.

If they hadn't been caught in the first place, it might have been fine. But after being caught, doing that would ruin their reputation.

Jinhaeru was a five-story, rectangular tower.

However, since each floor was as high as a story and a half, if you measured by the height, it was similar to or taller than a nine-story skyscraper.

It was also built on top of the Wolsusan hill, so when you climbed up there was nothing blocking your sight, allowing you to see even a thousand ri (approximately 3927 km) away.

Of course, it wasn't that you could actually see a thousand ri away, as that was just a way the people of Zhongyuan expressed it.

It was originally built as a watchtower and a military base.

However, after the military and administrative divisions were thoroughly separated, it became a public restaurant, and the most famous one in Guang Prefecture at that.

And it was said to boast a scenic view all the way to the South Sea at its peak.

At the special room of Jinhaeru, enclosed by folding doors, the special gathering of the Hwaryong Group began.

For reference, the Hwaryong Group was named by taking one character from the Black Dragon Group of Team Leader Jo Hakche, and one character from the Mount Hua Sect of Deputy Leader Changbin.

The reason it was called the Hwaryong (Splendid Dragon) Group instead of the Black Dragon Group was because Jo Hakche, who was very manly in front of men, readily yielded the first character to him.

Of course, that manly Jo Hakche was now regretting it, becoming a petty person.

He should have just called it the Black Dragon Group instead.

"Well then, have a drink. I'm sorry. You were supposed to be pinching some cheeks and having fun, but I butted in when I didn't need to."

"No, not at all! It is an honor!"

Soho, a disciple of the So Un Sect, politely raised his glass.

Cheonhwa Sword was not only a beautiful woman but also a high-ranking elder holding a position as a Daoist sect leader.

As he politely held up his cup to receive her offering, her white and slender fingers that were wrapped around the liquor bottle were so beautiful that it was like she was shouting, ‘This is exactly when the word ‘fair hands' should be used'.

Without realizing it, Soho raised his head to face the kindly smile (because of the food and alcohol in front of her) of the lovely yet dangerous Qing.

At that moment, Soho let go of all his regrets.

When the most beautiful being under the heavens offers a drink, how could a hundred gisaengs, no matter how much they tried to be charming, even compare?

Coming to the Hwaryong Group was the best decision I've ever made.

No, wait, being born was the best……

"You punk Soho……."

If it weren't for Jo Hakche, who was grinding his teeth, he might have stayed there, petrified like a stone statue.

Qing filled everyone's cups as she went around, and then she took on the role of a master of ceremonies, setting the mood.

"Alright, then, let's start with a toast. I want to hear the Hwaryong Group Leader's toast. Well then, Young Master Jo, a toast. Let's all welcome it with applause and cheers. Cheers, cheers."

"Ahem. It was hard getting all the way here, and then thank you so much for gracing us with your presence, Young Lady Ximen. You are truly beautiful and with the eyes as lovely as a lake, and this Jo Hakche, though it might be embarrassing to say, seems to have already fallen for you and I'm so sincerely grateful for you gracing this precious occasion with your presence, and since Young Lady Jin has also joined us here, and the two of you, who are the very image of the beauty of the Martial World, and, ah, Young Lady Gyeon too, of course, I do not mean one is less or more than the other, but the Cheonhwa Sword is graceful and beautiful, while Young Lady Jin is dignified, and also—"

"Ahhh, my arm is going to fall off! Anyway, cheers! Wishing for the eternal prosperity of the righteous world of Wulin!"

"Cheers!"

Even at a drinking party, their mannerisms differed based on personality and disposition.

For example, Changbin never moved and when women weren't present, his courage and voice were as loud as a roaring tiger, but when women were around, he would shrink, becoming similar to a broom that had been leaned against a wall.

Of course, that was not for any other reason, but because when women were present at drinking parties, the taste of alcohol was incredibly superior, so he would instead focus on being a good drinker.

Jinsul always preferred listening rather than talking.

Although Jinsul, who led the fashion in Dragon Phoenix Alliance clothing, was always surrounded by a never-ending stream of female experts, all seeking her opinion, she was fundamentally serious and tended to listen to others.

And then there was Gyeon Pohui, who had little interest in those outside of her circle.

When she was in the Bliss Palace, the Bliss Palace was that circle, and now, her family and the Seolga Merchant Association were her new circle.

Therefore, she just followed Qing and viewed the young men of the Orthodox Faction as no different from mere passersby.

It was also the reason why she had little interaction with Tang Nanah and Jegal Ihyeon when they had traveled together; she had been indifferent to both of them.

And so, she was only focused on Qing, sticking close by, refilling her empty glass, and putting snacks into her mouth.

And when a drinking party opened up, Qing became a human grasshopper.

She never stayed in one place, skillfully and naturally inserting herself into various tables, giving and taking drinks, quickly gulping down four or five drinks and talking quickly before saying, ‘Ah, I'll be going over there', sweeping through everything like a swarm of locusts who had emptied the field of its vegetation.

Thus, Changbin became uncomfortable.

He thought that since Jinseol, Qing, and Gyeon Pohui were a trio of women, the three of them would have something to talk about, and then he could quietly have a drink.

But then Qing suddenly left her seat, and Gyeon Pohui followed after her, leaving Changbin and Jinseol alone at the table, where silence descended.

Since Jinseol preferred to listen, she didn't open her mouth, so Changbin could only eye her, nervously worrying that Young Lady Jin might be uncomfortable and that he might be boring her. He had to say something, but what should he say? He had some interesting stories that he had heard before, but why couldn't he remember them………

"Uhm, Young Lady Jin? Does the food suit your taste?"

"Huh?"

Jinseol ended up asking back without realizing it.

What the hell was that supposed to mean? Was he asking a Cantonese person if Cantonese food suited her taste?

But Changbin was now feeling a great sense of accomplishment.

Good! I broke the ice!

"It seems that Southern food uses precious ingredients. Even this Palbo has abalone and octopus, shrimp, sea snails, and, ah, this, uh, this is……"

"That's a tilefish."

"Ah. You know it well."

"Well, of course, how would a Cantonese person not know Cantonese food?"

"Ah. That's true. Uh, sorry about that."

And then he closed his mouth.

Qing would be back at any moment so he nervously rolled his eyes around.

Meanwhile, Qing was having the time of her life.

"Alright, make some room over here. Nice to meet you, you know me, right? Cheonhwa Sword. Right, let's all have a drink. What's this? What is in this cup? Why is there moisture left in the cup? Wow, you're drinking very generously. Alright, let's all have a drink. Nice to meet you. Ah, Daoist Yuhyeon, you were here? Young Master Sang? Right, let's all toast. Cheers?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And in another special room of Jinhaeru, a grand banquet was taking place.

It was the Moon-Cutting Gate's faction dinner, where the executives of the Moon-Cutting Gate had all gathered.