\chapter{Telepathy (11)}

Inside a neatly carved stone grotto.

A young man was sitting, leaning casually against a giant stone chair carved into the wall.

The young man's epithet was Heart-Eating Demon Lord.

Or rather, according to him and his subordinates, it was also called Soul-Devouring Demon King. He was an old young man.

"Has the Blood Demon been completed yet? Hey, you monster, connect me to that bastard."

"That bastard… You mean, hmm… If you're referring to the bastard that the Demon King calls a bastard, ah! I'll contact the Alliance Leader. Ah, Sahui, is that bastard there?"

"No no no! You idiot! I'm not talking about the Alliance Leader! This bitch is trying to kill someone."

"If not the Alliance Leader, then the Thousand-Heavenly Emperor? Ah, I'll contact the Thousand-Heavenly Emperor. Ah, Dongil, is that bastard there?"

"Not the Thousand-Heavenly Emperor! When have I ever contacted that bastard!?"

"But you just said ‘that bastard'. How am I supposed to know? Ah. Is it that bastard, the Solitary Venerable? Hey, Cheonje, is that bastard there-"

A precious golden apple from winter flew through the air and struck the woman's solar plexus before shattering into pieces.

With the remaining force, the woman flew into the air and crashed hard against a stone wall.

A huge cloud of dirt and dust rose up.

However, the woman, as if she was completely fine, boldly raised her upper body and sat down while extending her legs forward.

"This is why I lack motivation. I'm someone who helps the Demon King to the very end, not the Demon King's subordinate."

"What are you saying, you monster bitch? You're acting as if you don't know on purpose, as if I won't know, huh?"

"You always call all men ‘that bastard.' I'm too dumb to distinguish between them."

"Whatever. Call that Bang bastard."

"Yes yes. I'll call that Bang bastard. Hey, Rangrang, is that Bang bastard there?"

The woman sat there blankly.

Then after a while, she answered.

"They say that Bang bastard is dead."

The Heart-Eating Demon Lord was startled.

"What!? Why? Who? What about the Blood Demon?"

"Startled, his fat rear end rose about an inch from the throne while saying, ‘What? Why? Who? What about the Blood Demon?'"

"I told you to remove that disgusting title. I wouldn't know if this monster bitch is playing with me or-"

"While grinding her ugly teeth, she said, ‘I told you to remove that disgusting title. This beautiful and lovely woman wouldn't ever play with me.'"

"Haa…… Never mind."

"Strategist Bang was beaten while trying to assault a woman, and then was killed by Wang Woo, the former Chief Manager and current Sect Leader of the Blood Moon Sect. As for the Blood Demon, I'll convey Rangrang's answer verbatim."

The woman cleared her throat and did a good job of imitating Rangrang's expressionless voice.

"‘This Rangrang does not know about the Blood Demon and does not wish to know about it. And this Rangrang agrees with the Demon King's opinion that Suran is beautiful and lovely.' That's Rangrang! That's Rangrang for you! How touching! I am moved! So deeply moved!"

"Those monster bitches are fooling around again! So is the Blood Demon completed or not!? If you don't know, then you should go and find out!"

"While her face, which had been stretched to get rid of wrinkles, wrinkled again, she said, ‘Oh dear, these precious ladies. Has the Blood Demon been completed? What is it? If you do not know, then after you find out, would you please share your profound insights with me?'"

The woman, Suran, asked and answered on her own.

"‘This Rangrang's assigned task is to act as the bodyguard and liaison for Strategist Bang. This Rangrang is obliged to fulfill the orders or requests of the Soul-Devouring Demon King.' That has been noted."

The Heart-Eating Demon Lord's expression became distorted.

"How can there be such irresponsible words!? Should I talk to that Un'ga bitch in person for her to listen!?"

"Demon King. When she asks us for help, she doesn't make us do it for free, you know? Ah. How kind she is. She's so warm to even our kind of failed results."

"Haa. Okay. So you want a payment?"

"For my reward this time, she hugged me tight for a full hour. And she also stroked my head, and kissed my cheek. Kyaaaa, what do I do? I'm so embarrassed."

"You're not even seven years old."

"And for your information, Rangrang said that she'll listen if you kneel and beg."

The Heart-Eating Demon Lord was taken aback and asked.

A monster who said she would listen if he knelt down and begged was currently performing her task.

Did that mean he actually did kneel and beg?

"No, seriously, what is this? It's not like I'm dealing with children. I can't even use the Jiangshis I've created. Do I really have to humor you all like this? Ha. This is ridiculous. Ha. Well, if you monsters wanted, you could rip apart that frail bitch with your fingers anyway."

At that, Suran showed a meaningful smile that was quite obviously suspicious.

"What I mean is, what each of us wants is all different. The Demon King cannot pay me, because there's nothing I want from the Demon King? If it was Rangrang, maybe she'll listen if you personally go there, kneel down, and beg?"

At that, the Soul-Devouring Demon King snorted.

"Whatever. Tell that monster that if the existence of those unfinished Blood Demons are leaked, it would greatly hinder our grand plan. If that Un'ga bitch doesn't want to take the blame for that, then get rid of those failed results now."

"Wow, that's so cruel. My Unni always cherishes us, even if we are considered a failure. How can the Demon King be such an unfeeling person? Do you not know what responsibility is?"

"Hehe, you monster bitch. Responsibility is something for the weak to take. The strong do not need to take responsibility for anything. If that Un'ga bitch was as strong as the Alliance Leader, would she have even pretended to care about you monsters?"

"But she would still be kind, though."

"Fine. If you don't want to see that Un'ga bitch you adore so much suffer, tell that monster to get rid of those failed results now."

At that, Suran blinked her eyes.

And after a long moment, she replied.

"‘Understood. This Rangrang will seriously consider it. Are you all set to go now? Me? This Rangrang is communicating with a colleague that exists somewhere in the world. It is not that. It is not an imaginary friend. And they are not a friend but a colleague. This Rangrang does not lack friends but does not need them.' What? She stopped there after making me curious. Did Rangrang finally make a friend?"

The Soul-Devouring Demon King shook his head.

"I don't need to hear things that are irrelevant. Anyway, did that monster say she would take care of it?"

"She said she'll try. Ah, by the way, Demon King."

"No."

Suran pouted.

"I haven't even said it yet."

"Is it that you want me to be your friend? Would I ever become friends with a monster bitch like you? Not a chance."

"Hmph. I don't need it either, you know? I won't be friends with irresponsible trash. Hmph. Hmph."

At that, a vein popped out on the Soul-Devouring Demon King's forehead.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Although she had heard about the pitiful situation from Jo Hyeong, there was something about Rangrang that felt, how should she put it, unsettling.

After thinking about it, she thought it might be because of her expressions.

Although the defective bamboo wife doll had a faint expression, she wasn't completely expressionless.

When she ate something delicious, her lips would curl up, and when there was no soup at the table, her eyebrows would droop slightly, showing a sad look. And when it was hot, she would sweat, but also look at Qing with a longing expression as if she were looking at a dog treat.

Hmm, come to think of it, I kinda miss the doll, too.

Anyway, but what about Rangrang?

Just as she had said, her emotional state couldn't move her facial muscles.

She was completely expressionless, without even a slight twitch.

It was eerie, like she was not human.

It was like something she had heard about in her hometown, how people became like that when they were traumatized. Or maybe not.

Was that something that had only come out of stories?

Or was there really a case where trauma manifested in that way?

But no matter how much she pondered about the facts of her homeland, there was no way for her to find out.

However.

After waking up early in the morning to the sound of someone conversing with a soft, monotonous voice, she came out and found Rangrang talking to someone.

Who could she be talking to at this hour?

When she went outside, she found Rangrang sitting on the floor, muttering to herself.

"Rangrang? Who are you talking to?"

Then, she said that she was communicating with a colleague that existed somewhere in the world.

"Ummm……, it's like an imaginary friend or something."

"It is not an imaginary friend. And they are not a friend but a colleague. This Rangrang does not lack friends but does not need them."

It was a tearfully pitiful excuse.

Well, she did have a family that was killed, and it must have been hard for her to survive all alone.

Originally, Qing was weak to kind people, and even weaker to the elderly.

And especially to kind people who were mentally ill, Qing was a person who could become as warm as a briquette.

"I'm being generous. Then I'll be your friend. We're friends now, okay? I'm not going to use polite speech from now on."

"Is it you and Rangrang? Rangrang's popularity is truly something. Rangrang is a bewitching woman. If you truly wish to become friends, if you kneel and beg, I might grant you the exceptional opportunity to increase your status from an acquaintance to a friend. It is an opportunity you will never have again, Heavenly Flower Sword."

"That's up to Rangrang, though. I've already raised you to the level of friend in my heart, so you can raise or lower your own rank as you please."

At that, Rangrang's eyebrows moved up, down, up, down.

"What, did it move?"

"Rangrang's problem is that her emotions do not connect to her expressions. It's not like her facial muscles have become paralyzed. Rangrang's facial muscles move as Rangrang pleases."

"So that means you can make expressions, right? So why don't you make an expression or something?"

"How do you breathe, Heavenly Flower Sword? When do you swallow your saliva? Where do you place your tongue? Where is your jaw, and how should your teeth be aligned? How many times do you blink your eyes?"

"Ehh. Agh."

Oh shit. I've been had.

Qing realized that she had fallen for a cunning and despicable trick.

Breathing, the position of her tongue and jaw, swallowing saliva, and such were things that were easy and natural when they were being done unconsciously.

But once one started paying attention to it, they would start to control it with their consciousness, making it awkward and uncomfortable no matter what they did.

"The same is true with Rangrang's expressions. It is impossible for Rangrang's objectively outstanding brain to take into account and display appropriate expressions for every single reaction."

"Umm…… Did I say something wrong?"

"If Rangrang was prone to negativity when it came to her current inability to make expressions, it would have been an insensitive remark that would have caused a big emotional wound. Fortunately, this Rangrang is not attached to such things, so I'm just giving an objective explanation."

"Hmm. Are you really okay?"

"Based on the Heavenly Flower Sword's earnest request, I will tentatively register you as a candidate for friendship. To rise to the rank of friend, a very high level of devotion is required. Devote yourself to this Rangrang. This Rangrang is currently craving tangerines."

"Oh. So you're a friend who likes tangerines."

Qing got up from her seat and turned around.

"Heavenly Flower Sword. The kitchen isn't in that direction."

"Huh? I'm going to sleep. Rangrang, you should also stop talking to your imaginary friend and go to sleep too. Sleeping is the best way to pass time."

"While I agree wholeheartedly with your opinion, if Heavenly Flower Sword goes to sleep, who will bring Rangrang tangerines? And who will dispose of the fruits that are not sweet enough? And what about proving the hypothesis that Heavenly Flower Sword is capable of eating even the tangerine peels based on her gluttony?"

"Can't you just ask if they have any in the kitchen?"

"Your attitude is incredibly poor. You have been rejected as a friend. You must again speak to Rangrang with respect and proper etiquette, Heavenly Flower Sword."

"I don't wanna? Even if I'm rejected as a friend by Rangrang, I've already accepted you as a friend on my end, so you can raise or lower your own rank as you please. And if you really hate it, you can kneel and beg while saying, ‘Please, don't consider me as a friend,' and I might allow it."

At that, Rangrang clapped her hands.

"Is this the principle of Tai Chi? Is this a move worthy of a divine dragon? This Rangrang has achieved great enlightenment. I'll give you one point towards friendship."

"Out of how many points?"

"Out of 10,000 points."

At that, Qing let out a hissing laugh.

She was just a woman who was unique in a few ways, but still just a woman with a nasty temper.