\chapter{Telepathy (4)}

It was an incredible situation, where an Orthodox Faction and an Unorthodox Faction were hosting banquets side-by-side on the same floor of Jinhae Tower, a single tavern, and that too, divided by only a sliding door.

But who could blame?

It wasn't possible to blame the owner of Jinhae Tower.

If the Wulin Alliance's Hwaryong Squad had arrived first, then it might have been a different situation. But strictly speaking, the first customers were the members of the Salwol Clan's executives.

And yet, suddenly, martial artists from the Orthodox Faction barged in, asking if they had a good spot on the top floor.

Not only that, but Jin Seol was among them.

So, from the Tower's owner's perspective, it was a situation where he absolutely could not mention anything about the Salwol Clan.

Should he say ‘Because I had to accommodate the Unorthodox Faction, I can't accommodate you?'

That would mean that you, and the Jin family, were not as good as the Salwol Clan.

It was not a problem of whether or not to accept them.

Even mentioning it was the problem.

Even if he only mentioned to be careful or to pay attention, it could still be taken as a serious insult, so the best they could have done was say that there was no more room and turn them away.

However, the special room reserved solely for the Gwangdong Jin Clan was occupying a prominent spot on the top floor.

It would have been even stranger if the special room reserved for the Jin Clan was empty.

In other words, it was a situation where there had to be no available seats.

So, what to do?

They could only overcome it with the power of prayers.

‘Buddha, the Jade Emperor, and Confucius. Please, please, please, let nothing go wrong,' they asked.

If a crow-tit wished to chase after a white stork, it should not attempt to compete in running, at the very least.

Originally, in any competition, one must highlight their strengths while exposing the opponent's weaknesses in order to seize victory.

If a crow-tit wanted to beat a white stork, it should hide its size and compete with its cuteness.

However, Gyeon Pohui wasn't that smart of a person.

And so, she had no idea what would happen if she chased after Qing at such a banquet, who was essentially a giant of drinking, the embodiment of alcohol, and the white stork of drunkenness.

Ah, so happy to meet you. Happy to meet you, so let's have a drink?

If we know each other's face and name, we're friends, so now let's have a drink as friends.

Now, those who are tired, close their cups. I'm still completely fine, I can have more, let's try to drink one more cup from the Heavenly Flower Sword, is that all? You're a man, a man, and a hero. Cheers. Cheers cheers!

Ah, that table over there looks left out. Please have a good time for a moment while I quickly go there. Then, for now a brief goodbye, a drink of parting? Yes! Cheers!

And then, she would dash off again, holding a single cup while saying, "What are you all talking about? Oh, sorry, pardon me. Hehe, happy to meet you, let's have a drink first……."

And so, by the time Qing had gone around the banquet twice, calculate the amount of alcohol the Spiritual Sister has drunk.

Gyeon Pohui was someone who naturally had to accept the alcohol Qing was giving.

Because, it was rightfully her share.

It was alcohol that she was giving to even people she barely knew.

So, she absolutely could not afford to not receive it.

As such, she would stick right next to Qing, chugging cup after cup of alcohol.

As if she was worried that others would receive more than her.

"Ah, Changbin looks bored. Ah, I did promise to pour him a drink. I'll go there for just a moment, okay? You can't be passed out when I get back."

Qing said so with a cheerful smile and headed towards Changbin's table.

It was towards Jin Seol, who had a face that seemed to be boiling in anger, Jo Hyeong, who was clearly the cause of it, and Changbin, who was merely staring blankly at the glass, bewildered by such a peculiar object.

It was then.

Suddenly, Gyeon Pohui wrapped her arms around Qing's neck and threw her body at her, or rather, threw her body at her and clung onto her.

With her neck held in a death grip and hanging onto Qing, Gyeon Pohui rested her chin on Qing's chest and looked up at her.

"Hehe. Sworrrnn Siisssster."

Qing was shocked.

Gyeon Pohui had never leaned on Qing before.

She never did anything that could make Qing feel uncomfortable.

So it was a one-sided relationship where only Qing would lean on her, hug her, grope her, and do all sorts of antics. Seeing Gyeon Pohui clinging onto her with her full weight was a sight that even Qing was seeing for the first time.

However, even though Qing was shocked, she was not confused.

After all, nothing was out of the ordinary at a drinking party.

"Ah. Spiritual Sister. You okay? You've been drinking a lot, you know. Aren't you drunk?"

"Huh? Yeah. I guess I'm drunk. I'm druuuunk. Hehe."

"My goodness. Just look at those glazed eyes. You kept drinking despite not being able to handle it? Spiritual Sister? I should exorcise the effects of alcohol, ah, wait, not here."

If a martial artist had properly trained, then they would be able to drive out the effects of alcohol with Qi Circulation.

However, expelling the effects of alcohol at a drinking party was an extreme breach of etiquette.

When the effects of alcohol, even more toxic than any alcohol, were expelled, the smell of alcohol would start to linger around in the air.

The alcohol that was released like steam itself could inebriate those who were weak drinkers.

So if one felt like they couldn't take it anymore, they would go outside, to a spacious place with open air, and exorcise the alcohol before returning.

"Then where?"

"It won't do. I need to go out and get some air. Let's go get some air for a moment."

"Yes. I don't like wind. It's cold. But you want to get some air, right? Let's go quickly."

"Okay, okay, don't lean, ahem."

"Ah. No. I can't lean on you. Sworn Sister has bad legs, so I shouldn't. But, umm, it's uncomfortable. Frustrating. What is this? It's too cramped."

"It's not like your chest will be pushed back if you lean on me, okay? Seriously, stay still."

"Hehe. Okay. Ah. How nice."

Gyeon Pohui buried her face in Qing's neck and giggled like a fool with a silly, loose smile.

Upon opening the sliding door and leaning against the railing of Jinhae Tower's watchtower, the salty sea breeze caressed their skin.

In fact, even though it was winter in Gwangdong, it felt like spring to Qing.

Guangzhou was a place that, even during the coldest nights of winter, was over ten degrees Celsius, feeling warm and pleasant, while also having brutally hot and humid summers, feeling akin to being trapped inside a steam room.

Of course, Qing had already reached a near-unaffected state.

If one were to stand on the highest watchtower in Guangzhou, where the harsh sea breeze blasted, unless one was a person like Qing or the Seol Clan, they would just feel cold.

"It's cold."

"Okay. Let's get rid of the alcohol and hurry back inside."

"Yeah. No."

"Eh?"

She had taken a completely unexpected turn.

What is this? Does the Spiritual Sister's personality change into being rebellious when she's drunk?

"Jiejie\footnote{Unni/ older sister}. Call me Jiejie. Do it quickly."

"Umm. That's a bit…"

"Then I won't go. I'll just stay here. I'll shiver all alone here from the cold. If I freeze to death, Sworn Sister will cry in sadness later, guhuk."

"Ha. Seriously."

"So, please, hic, quickly, Unni. Unni, please do it. If not, I'm going to freeze to death here and, hukh, heuugh."

"Sworn Sister, stop it. No, I mean, why is an adult crying?"

"I'm not Sworn Sister. I'm Unni. Do it quickly."

"Oh, umm."

Qing's mouth opened and closed.

Perhaps it was because of the strong wind, but goosebumps rapidly spread from her arms throughout her entire body.

I would have preferred that asshole calling me mother.

Saying Unni herself was not only impossible to pull off, but it also gave me goosebumps, and my heart was pounding, and my fingers were twisting on their own, like some kind of butterfly knot.

Qing tried to subtly gloss over it with a joke.

"Sworn Sister should live here. I'm going home."

"Nooo. Why? Why? W-Why? Is it because I'm not Unni-like enough? Is it because I'm a stupid bitch?"

"It's not like that. Wait, hold on. A stupid bitch? Who dares to call my Sworn Sister that?"

"No. I know that I'm stupid too. When I was in Bliss Palace, the Senior Sisters always said so. A stupid and insufficient bitch. Uh. Huk. Even Sworn Sister is ashamed of that, right? You're just a fake Sister, after all. Uh."

And then, she started tearing up.

Qing realized that she was caught.

She had merely been calling her Sworn Sister because it was physically impossible for her to say anything else, but that was something she always had in her heart.

Qing let out a deep sigh.

At that, Gyeon Pohui, startled, hurriedly wiped her tears away.

"No, hehe. I'm not crying. Am I drunk?"

"Sworn Sister?"

"Agh, you, did you think it was annoying? Ah, do you, want to feel my breasts? Sworn Sister likes my breasts, right? Here, uh, wait, I can't untie this, just, wait."

Gyeon Pohui started to undo the front of her clothes.

However, perhaps because her hands were trembling, or she had accidentally pulled too hard, the string was just tightening even more, making her struggle.

At that, Qing placed her hand gently on the back of Gyeon Pohui's hand.

"Sworn Sister. No. Hufffff."

Qing took a deep breath.

"Jiejie."

At that, Gyeon Pohui's eyes widened and her lewd gaze that looked out of place, was nowhere to be seen as she looked at Qing with perfectly round eyes.

"Can you see this? The goosebumps I have? There's a personal problem why I can't say Jiejie. It's not that Sworn Sister is… um, actually, it is a little bit embarrassing. That a grown woman is crying and all, showing off her chest at a place like this, without any shame."

"Yeah…….."

"To be honest, tell me. Do you think I'd think of Sworn Sister like that? Are you going to think I'm only that kind of person?"

"Not a guy but a girl-"

"Ahem, anyway."

"……No."

At that, Qing smiled brightly and stroked Gyeon Pohui's head.

"Actually, it's an embarrassing Jiejie, not good enough to bring outside, but I've never hid you away, have I? Even back inside there. The Heavenly Flower Sword has Gyeon Pohui as her sworn sister, and I've never hidden that. I won't in the future either. Whether it's embarrassing or shameful, Sworn Sister is my Sister and, yes, family."

"Yeah…… But is it still embarrassing?"

"In family, we don't lie."

Gyeon Pohui's expression became ambiguous.

She was happy that they were family, but on the other hand, it was complicated. Is it really embarrassing, for real?

"It's okay if you're stupid. I like Sworn Sister even if you're like that. You're cute, and you're also so useless. I like a Sworn Sister who always cares about me with all her heart a hundred or a thousand times more than a Sworn Sister who is smart and pretentious."

"One hundred and one thousand……"

"Why are they so obsessed with putting a number after it in this damn Zhongyuan? Sworn Sister, or, then how about Gyeon? Or is it a bit weird that I'm emphasizing that our family names are different? Then should I call you Hee? Which one do you like, Hee or Yi-mei\footnote{also Older Sister}? Jiejie is too difficult for me."

"Then… Yi-mei……"

It seems she couldn't give up on being the older sister.

Qing smiled at her gently.

"Okay then. Yi-mei."

"Yeah!"

"You understand my heart, right? Alright. Then come here."

Qing hugged Gyeon Pohui tightly.

"Ah. By the way, if anyone dares to call Yie-mei a stupid bitch, you should just rip off their wrist, no, wait, will that even work? You should just break their hands off so they become a cripple, and tell them. ‘Even though I'm stupid, what have you done that's so great?! I might be stupid and useless, but that's my charm, you know? Do you even know what beauty in foolishness is!'"

"Beauty in Foolishness?"

"Originally, beautiful people are actually better when they're foolish and lacking, you know? I like my Yi-mei, who is so useless so much more than someone smart and pretentious. She's also very affectionate. And since I'm smart, it's okay if Yi-mei's stupid, right?"

"Huh? Yeah, I guess so. Hehe."

"Okay. Then let's exorcise the alcohol and since it's not really cold, it's also a bit awkward to be outside. Let's go in."

"Yeesss. I want to go into your sleeve first. Are my eyes red? I'll go in after resting for a bit."

Sleeve. It meant younger sister.

Even while continuously thinking about the meaning of the word ‘sister', she couldn't call her sleeve, showing just how much she had suffered on her own.

I did not reassure her enough, it seems.

Qing reflected a bit.

Just a bit.

To be honest, wouldn't it be much more her fault for being dumb and ignorant, thus misunderstanding everything?

So if we really had to go into who's in fault, it would be a ratio of one to nine. Of course, with Qing being the one.

"Okay. Don't stay out too long. You'll catch a cold."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had told Gyeon Pohui that if anyone dared to call her a stupid bitch, she should rip off their hands.

Of course, this meant she shouldn't just stand there and listen if someone was cursing her.

But the person who heard it was Gyeon Pohui.

As such, Gyeon Pohui was extremely impressed.

As expected of my sleeve, my sleeve always has a plan. How did she know this would happen?

Did she perhaps foresee the future?

"Gurgle."

A man lay sprawled at Gyeon Pohui's feet, foaming at the mouth.

His arm was twisted in a pretzel shape, bent at an angle of half a turn, leaving a lasting impression.

Gyeon Pohui looked down at that man.

With eyes devoid of any interest, just like looking down at any ordinary stone lying on the street.

"Ah. I should wait for my sleeve."

Gyeon Pohui turned her body around and walked down the long corridor that extended out of the double sliding door. Then, she suddenly stopped.

She then turned back, cleared her throat, and said:

"Did you have something to say about me being stupid, huh? Well I'm beautiful, stupid, and useless, so that's my charm! Know that? I'm beautiful because of my stupidity."