\chapter{Telepathy (5)}

Strategist Bang, Bang Jeommyeong, was ecstatic.

It had been a long time since he had received a drink from a courtesan, and before the first toast could even be made, his wicked hands were already groping at the courtesan's chest.

At that, Yi Wangchul, the sect leader of the Slaying Moon Sect, said, "Well, it's not like the courtesan is running away. He must have been starving for a long time."

He also thought, "Isn't he a man who enjoys the affections of men? For some reason, he was giving me dirty looks. Or maybe that maid he kept with him was actually his concubine, and her constant fawning showed that he was being tightly controlled. He's truly embarrassing all men."

Since Strategist Bang never came to the group dinners, increasingly dirty rumors had been spreading.

But seeing his behavior today, those rumors were likely to be completely dispelled.

However, his manner of clinging to them like a wild man who had been starving for ten years was a bit much. As the strategist of the sect, he should have at least maintained some decorum.

At any rate, the Slaying Moon Sect's group dinner was enjoyable.

It was truly enjoyable.

They enjoyed it in a rowdy, lewd, and all-around unhealthy and unsanitary manner.

It was truly a feast for beasts!

Human disqualification! Beast qualification!

Then, suddenly, Strategist Bang staggered and got up from his seat.

"Aigo."

"Strategist Bang? Where are you going?"

"I'm just going to relieve myself…"

At that, Wang Woo, the former head manager and current head instructor of the Slaying Moon Sect, spoke with a sly, meaningful smile.

"Aah. Is that so."

At that, the thugs of the Slaying Moon Sect snickered.

The Unorthodox Faction were prone to obsessing over utterly useless things in life.

One of them was their tolerance for alcohol.

While the orthodox martial artists would drink moderately and stop when they thought they might make a mistake, or go out for a walk to sober up, the unorthodox bastards would keep drinking until they dropped dead.

It was because sobering up wasn't manly.

A man should never spit out the liquor he has drunk, even if it meant dying from being drunk, or so they believed, a strange obsession indeed.

As such, a vein bulged on Strategist Bang's forehead.

"It's not that, I'm just going to relieve myself."

"They all say that, but then they always come back with perfect complexions. Isn't that right? I mean, what is with all those excuses like they are women, before spitting out the liquor they had just drunk."

"Hmph. Then why don't you come with me and see for yourself."

"What would I do looking at a man's cock? I'm just going to count how long it takes you to come back. If it takes too long, you know?"

"My pee stream is as long as the Yangtze River, so why don't you come and hear it for yourself. You'll be so blown away by the sound of it crashing down like the heavens have opened up. Alright everyone, if Wang Instructor starts rushing back later and making a fuss about how the heavens have fallen, just know that my pee stream is at that level."

At that, laughter erupted from the crowd.

Wang Woo's face contorted as if he had bitten into a rock.

What could he do? He had tried to win a debate with a strategist who lived by his brains using only his brawn.

Having easily defeated Wang Woo who had needlessly instigated a conflict, Strategist Bang opened the sliding door and swaggered out with his shoulders raised high.

He looked left and right, checked the empty wooden sign that indicated the toilet, and took one step, then two steps.

Then, suddenly, along with the sound of a door sliding open, a pale face appeared with a blank expression.

"Consumption of alcohol exceeding one bottle. You have broken our promise. You are a liar."

"Agh! You scared me! What the hell, when did you get here?"

"I was in the middle of a mission. You have far exceeded the amount of alcohol you promised to drink. This is a serious act of deception."

"Hmph. Aren't you also loitering around under the guise of a mission? Why don't you wipe off that stain on your mouth?"

Langlang's usually expressionless mouth was covered with bright orange oil stains, and on her left cheek was a long streak of thick black liquid, probably from eating some kind of grilled skewer.

"It was merely to replenish my energy in order to perform my mission. Anyway, this Langlang will consider this an active act of deception."

"Hmph, so that's why I'm going to relieve myself right now. As long as I'm not drunk, it should be fine, right?"

"Do as you wish. Do whatever you want."

At the same time, Langlang slammed the door shut.

Strategist Bang clicked his tongue.

"What? Is she sulking? Ha. How ridiculous. She's a monster, a zombie-like bitch who isn't even human, yet she's trying to imitate humans. A zombie that eats expensive food, huh."

Strategist Bang grumbled as he walked down the hallway.

Then, suddenly, a woman slipped out of the toilet.

Strategist Bang, forgetting his need to relieve himself, stopped and blankly stared at the woman.

Her beauty was so lewd that she had to be a courtesan, but truly, how could there be such a top-tier, no, a super-duper top-tier courtesan in such a backwater town?

Strategist Bang's misunderstanding was not unique.

When it came to the beauty standards of Zhongyuan, a lewd-looking woman was a source of shame, so they covered themselves with heavy makeup.

However, there were women who didn't hide and boldly displayed their beauty; these were women who seduced men, courtesans.

"You, you. What is your name?"

Gyeon Pohui stared at the middle-aged man who had suddenly started talking down to her.

Gyeon Pohui's way of thinking unfolded.

You have been spoken down to.

Are they old? No.

If not, do you know them? No.

If not, are they a Master? No.

"Me? I'm Gyeon Pohui, but who are you?"

Gyeon Pohui returned the insult exactly as it was given.

If it were to be packaged as a positive trait, it would be called a mirror, but to Qing, it just seemed childish.

"Ahem, I am Bang Jeommyeong, the strategist of the Slaying Moon Sect. Although I am called a strategist, I am practically the second-in-command."

"Slaying Moon Sect? I think I've heard of that somewhere. Yeah, okay? So? Why?"

"Are you currently occupied with a guest? No, never mind. What does that matter? How much will it cost? I will give you as much gold as you want. Here."

Then he grabbed Gyeon Pohui's wrist.

"What the, how can a woman have so much strength? Why are you still standing there like a log?"

Gyeon Pohui was a master.

She simply hadn't responded to the weak attempt of a low-level punk who was barely considered to be in the First Rate Realm.

Gyeon Pohui tilted her head, feeling the weak force of the hand pulling her wrist.

"Where are you going?"

"Hehehe, if a man and a woman meet, what else is there to do? Hehehe."

Gyeon Pohui tilted her head again.

"What do you do when a man and a woman meet?"

"What? Are you asking when you know? You pour drinks, you kiss, you know?"

"Why? I don't want to?"

"What is this? Why are you acting like you're an idiot? If this esteemed one tells you to come, you should just say yes and follow me. Are you saying I should forcefully take you? If you come with me with good intentions, you'll be spared all the trouble, so why are you acting like a fool, you stupid wench?"

The moment Bang Jeommyeong said that and yanked her hand roughly…

All resistance she had displayed until now was nowhere to be seen, and she was pulled right in as if the hand that was pulling her had no weight.

And then, the momentum didn't stop and suddenly turned into a force of a thousand keuns, rotating her arm.

The rotational force amplified from the elbow, then her shoulder, becoming an unstoppable, huge current that swung her body around.

Bang Jeommyeong's body spun like a waterwheel, with his arm as the axis.

It was as if the top and bottom were grabbed and rotated, causing his mind to go hazy as the sky and earth spun wildly.

In the dim consciousness, Bang Jeommyeong barely recalled one of the legendary Divine Arts that followed a similar principle.

The Heaven and Earth Reversing Technique.

To grab and turn the heavens and the earth.

At that moment, she spoke to him with an icy voice.

"Did you add anything to my stupidity? What, like, I'm charming but stupid and worthless, a dimwit, you know what a dimwit is?"

It was a stupid sound that struck at his core, a sound that shattered the consciousness Bang Jeommyeong was barely holding onto, all in one blow.

As Bang Jeommyeong was feeling his consciousness fade away, his final thought was:

A dim beauty, you mean, you stupid wench……

Fortunately, Bang Jeommyeong was not left on the cold floor for long.

Since there was no news from Strategist Bang, who had said he was going to relieve himself, the Sect Leader of the Slaying Moon Sect told someone to go and find him.

After all, if a bookish man with a low tolerance for alcohol got drunk and fell into the toilet, it would be a disaster.

The one who offered to go was, surprisingly, the former head manager, Wang Woo.

"Manager Wang, no, I mean, Instructor Wang? You?"

"Elder Brother, I can't just keep growling like a dog, can I? We're all part of the Slaying Moon Sect, so I should give in this once."

Of course, Wang Woo didn't have such vicious intentions as killing him or anything.

He was sure that he had just passed out drunk in the toilet or some empty room.

So he was thinking of dipping him into the toilet and dragging him out, because if he was called a toilet-dwelling drunk, he'd be considered a moron, regardless of whether he was a strategist or not.

It was a thought that was almost better than killing him.

At least before the Sect Leader had added to it.

"Yes, my brother, well thought out. He's a small fry, but he's a vital talent, so we must treat him with care. You know, that's what a man should do. Here, take a drink to relieve your anger. I know you were upset. I just made it seem like I was listening to Strategist Bang since he is so narrow-minded, but I'll put you back in the position of head manager."

Yi Wangchul offered him the drink as if he was proud of him.

At that, Wang Woo, who had downed it in one go, grinned a ghastly smile.

Yeah, so that bastard was the reason I lost my position as head manager, huh?

It was the moment when he had finally acquired concrete evidence of what he had only inferred until now.

As he came out into the hallway, there was a drunkard sprawled out on the floor.

He thought he was just sleeping in the middle of the hallway.

But his eyes were rolled back, revealing the whites of his eyes, his lips were bubbling with foam, and his arms were twisted and mangled beyond repair for some reason.

Wang Woo's lips stretched up to his ears.

The untimely death of a colleague was a daily occurrence for the members of the Unorthodox Faction.

Looking at him, he thought, ‘This bastard must have messed with a Master and gotten his ass kicked'.

Wang Woo thought to himself that this was perfect, as he drew a dagger.

At that moment, Strategist Bang regained his consciousness.

"Ugh, Instructor Wang……?"

"You son of a bitch. Yeah, it's Instructor Wang. So you feel good now that I've been demoted to Instructor because of you, huh? You punk, you messed with the wrong person."

"It's not ‘demoted', but ‘slandered'… Keuk."

The blade that sliced past his neck made him grab it with his intact hand.

"Whether it's ‘demoted' or ‘slandered', the words ‘I'm sorry' should have come first, you fucker."

At that, Wang Woo spat on the ground, kicked the back of Bang Jeommyeong's twitching back, and turned away.

"Kkeureuk. Keureureuk."

Bang Jeommyeong desperately tried to scream, but it was impossible to make a sound while blood was rushing to his trachea from the cleanly cut wound in his neck.

He heard the sound of a door being opened almost as if it were being broken, and Wang Woo's urgent voice.

-Elder Brother! A disaster! A disaster!

At that moment, the sliding door in front of Bang Jeommyeong quietly opened.

Below the opened door, a blank face met Bang Jeommyeong's eyes as she rested her chin on both of her hands that were placed on the floor.

It was Langlang's face.

"This is why mutual trust and faith are so important. Because you can be betrayed at the most important moment. Do you understand?"

"Keureuk……"

"Unfortunately, this Langlang does not have the ability to infer conversations from human expressions. But from the shape of your mouth, you seem to be saying ‘Please save me'."

At that, Bang Jeommyeong's eyes filled with desperate light as he nodded vigorously with his slit throat.

And then, Bang Jeommyeong's pupils dilated.

It was because Langlang's face, which had always been expressionless and non-human, though she wasn't human to begin with as a zombie, had revealed emotion for the first time.

Langlang's lips stretched wide down to the bottom of her earlobes.

As such, she brightly revealed the sharp, jagged teeth of a monster.

"I have decided to no longer imitate humans, since I am, after all, a monster, a zombie that is not human. So, instead of asking this annoying zombie, you should ask the humans."

Then the sliding door slowly closed.

Bang Jeommyeong kept foaming at the mouth, making gurgling sounds with blood.

In his fading consciousness, a distant, urgent voice rang loudly.

Strategist Bang! What is going on! Get a hold of yourself! Blood, damn it, stop the bleeding! Shit. Some proper swordsman stabbed him, what the fuck. What excuse am I going to have to give to the Faction of the White Path…