\chapter{Telepathy (7)}

If one were to ask an Orthodox martial artist if it was necessary to uphold the dignity of an Unorthodox villain, nine out of ten would answer no.

But what if one were to ask if it was okay for a villain to die by being hit by a jokbal?

They would all show reluctance, and would say that it was a bit too much. It would be more honorable to kill them with a punch, than to use such cruel methods.

Because it was the worst method of killing that could make even death a laughing stock.

To die by being hit by a jokbal due to the lack of any other method, and especially a seasoned martial artist who was the master of a sect, dying by a jokbal?

Then what should be said at the funeral, and how should the survivors vow for revenge?

‘I will avenge the Clan Lord who died from being hit by a jokbal!'

‘I will eliminate that wicked enemy who wielded a jokbal against our Clan Lord!'

‘That bitch's jokbal will break before my sword!'

As such, Lee Wangchul faced a crisis among crises, an unprecedented crisis that no martial artist, no, no human being had ever encountered before. (Although primates would have faced similar crises frequently).

In the face of such a crisis, there were those who would give up and those who would grit their teeth and break through.

Lee Wangchul was definitely the latter.

As the leader of a faction, it was only natural.

At the moment when the smooth, shiny, clean pig's hind leg bone with no flesh attached appeared in his vision, Lee Wangchul's potential exploded.

It was a miracle brought about by the desperation that he could not die from being hit by a jokbal.

Even in a situation where the wooden floor had broken, making his footing unstable, Lee Wangchul put all his might into taking one step-

That's right! Just one step.

In that moment, the muscles of his entire body, the tendons controlled by the muscles, the bones attached to the tendons, and the joints that connected the bones all combined their strength for one purpose.

It was a majestic and harmonious chorus.

Too much was worse than not enough.

The exquisite distribution of power that pulled the bones and joints by large muscles was instead a grand move of a magnanimous person, who gave way to the smaller muscles and pushed their backs.

Thus, nameless small muscles all held his wavering torso with more power than they were capable of, as if exploding all at once, maintaining an unstable balance.

Thus, it was just one step.

It was neither urgent nor hasty, but just one step that was a natural phenomenon.

Whoosh. The rounded joint of the jokbal, falling vertically, grazed past the tip of his nose.

It reached the closest distance that would not allow even a single strand of hair before slipping past and dividing the air.

A casual step back, just one small step.

But for Lee Wangchul, it was a great leap.

At that moment, a grand enlightenment arrived.

True strength was not something that came by forcefully pushing through.

The distribution of the small and large, each moving for their own tasks, the different bones, different muscles, all of them completing their functions as one, only then can I finally utilize my body as a whole individual.

The Inner Qi he had forced into his body that was now holding it back.

This was called Essence (精), the energy held by a person.

The techniques he had only memorized by repeating them in his body.

This was called Qi (氣), the principle of utilizing matter.

The knowledge he thought he had understood through verses and principles.

This was called Spirit (神), the power held by the mind.

The boundary between the three, the ‘knowledge' of Inner Qi and the mind and body that merged into a whole. Complete understanding, that is, Oneness (一元).

Thus, it was a dramatic moment when a martial artist who had transcended himself now completely became one.

A sudden enlightenment.

The jokbal that had left suddenly came back.

Bam!

His head was blown open in one hit.

The brain of the great Unrestrained Realm Master escaped the shackles of flesh and experienced freedom for the very first time in the world.

It was the moment when an enlightenment that had come through a jokbal was blown away by a jokbal.

This was called Yushiyouzhong, the virtue of completing what you start, seeing things through to the end.

"Eh? What? Why are you standing still?"

Qing lowered the arm holding the jokbal, her expression bewildered.

What dripped red and splattered was not blood pudding.

She never even thought that he would evade the surprise attack, but he slipped away with some mysterious movement.

And then, he was standing there with an empty look, gazing at a distant place and standing there in a daze.

He wasn't even activating his protective Qi, so she had ended up smashing his head with a single strike.

What is going on? Well, whatever.

It didn't seem like someone who had had his brain blown apart would be able to live, so there was no way to know even if I did get curious.

As such, instead of wondering why the Clan Lord was in such a daze-like state, Qing just raised her voice triumphantly.

"The enemy leader! Has been defeated!"

The Saywol Faction warriors snapped back to reality.

"Clan Leader!"

The young members of the Hwaryong Squad also snapped back to reality.

"Let's eliminate the villains!"

But why was it that people shouted loudly after defeating the enemy leader?

Just as the presence or absence of a head determined life and death for a person, so too did the presence or absence of a head determine victory and defeat for a group.

Since the Clan Leader's head had been blown apart, the young blood of the Hwaryong Squad was literally surging to the sky.

The young members of Hwaryong Squad, charging while holding onto their weapons, were now intoxicated by the liberation that they had become true chivalrous men, the act they loved the most, eliminating evil, and the very self that was undertaking justice. And that confident pride was manifested into a Qi that cut down evil.

However, the warriors of the Saywol Faction, who had witnessed their Clan Leader's head being blown apart by a jokbal bone, were already terrified by the cruel methods.

It was such a vicious method that even mocked death itself!

Of course, Qing did not have such a malicious and evil intent.

She was just in a hurry, and it just happened to be in her hand.

Perhaps it was to slice the meat neatly, or maybe the chef was a novice, but there was very little meat attached to the bone, to the point that it looked just like a wooden stick.

After all, the meat attached to the bone was tasty!

Qing had been gnawing on it, making it all shiny and polished, so when it was needed in a hurry, how could she not swing something that was long and heavy in her hand?

If she left them alone, they would bicker and argue about the situation.

And since the way of Wulin always started with words and ended with blood, if fighting was unavoidable, it was better to break the leader's head first.

That way, they could protect Hee Mae and also minimize the damage to their comrades at Hwaryong Squad.

And that was exactly what happened.

The Saywol Faction warriors could not even properly clash their swords and immediately turned their backs to flee.

Sounds of them stumbling as they went down the stairs, the sound of crashing as they broke through the railing, and the screams of falling down in a hurry.

But the surviving officers of the Saywol Faction, who had attended the feast, were revealing their seasoned escape artist side, befitting of Unorthodox Factions.

Without tangling each other in the narrow corridors or on the stairs, they immediately broke through the paper doors and went to the opposite special rooms, then broke through the paper doors again and rushed to the railing, before leaping down without hesitation.

Jinheoru, a rectangular building, followed the architectural style of Zhongyuan, and in this primitive, ancient, uncivilized setting, it meant that it was narrow at the top and wide at the bottom, so they displayed a quick retreat to the ground by stepping onto the tiled roofs on each floor.

They were cold-hearted brothers who used their younger brothers, whom they had brought along, as bait and ran away.

Of course, ‘Agh, my brothers! I shall not forget your sacrifice!'

The officers of the Saywol Faction had already fabricated and forcefully implanted a memory in their brains of a heroic scene where they sacrificed themselves for the sake of their older brothers.

The greatest victims of this moment were not Lee Wangchul, who died from being hit by a jokbal, the officers of Saywol Faction who lost their precious direct subordinates, or the quick-witted escapees who at least saved their lives even if they were injured from stumbling down the stairs.

Lee Wangchul, at least, had tasted a bit of the great realm, the Unrestrained Realm, as a martial artist before dying.

And a dead person was no longer a victim, but more like a victimized corpse if one had to put it that way.

The fleeing officers, including Wang Woo, at least saved their lives and were able to escape the brutal jokbal attacks of the Heavenly Flower Sword.

And it went without saying that the Saywol Faction warriors, who were injured from tumbling down the stairs, at least managed to save their lives.

But what about the remnants of the Saywol Faction who were ransacking other rooms and yelling at the innocent guests in the private rooms?

They had no way to retreat because the stairs were blocked, and they were already unable to grasp the situation.

As such, the righteous youths of the Orthodox Faction, who rushed in with shouts, cut them down without mercy, screaming, ‘Die, you trash of the Unorthodox Faction!'

What was even more unfair was the reaction of the private room guests, who were cheering them on.

As expected of the Orthodox Faction! We believed in you!

Overwhelming gratitude! And more gratitude!

Thanks to all of you, we have avoided a great insult.

The Orthodox Faction is the best. We love the Orthodox Faction. The Orthodox Faction always does the important things.

We know you, Shaolin Sect, Nine Sects One Union, the Wulin Alliance.

It was truly a heartbreaking sound for the Unorthodox gangsters who were bleeding and dying.

We're all people who kill and eat like any other people, you know…

And the thugs of the Saywol Faction, who had been kicking, hitting, and striking with weapons against one woman, also met the same fate.

Or rather, to be more precise, they suffered a more bizarre and miserable fate than the others.

The number of those who died from being hit by a jokbal increased.

"How dare those thugs gang up on a woman. And those bastards who always talk about honor and pride! Are you okay? Young Lady?"

At that, a woman who had curled up her body and covered her head slowly turned her head.

As if nothing had happened, her expressionless eyes lay on the ground, looking up at Qing.

"Thank you. May I ask the name of the great expert who saved me, Lang Lang?"

"I'm called Seomun Qing."

"If it is Seomun Qing, is it Seo, Munqing, or Seomun Qing? Following the common naming practice of Zhongyuan, if you say it's the latter, are you the Heavenly Flower Sword, Seomun Qing?"

"Hmm. What kind of Heavenly Flower Sword are we talking about?"

"A monstrous being said to have three or five heads. But this Lang Lang has realized that those were merely misunderstandings of Lang Lang. You are not a monster with many heads, but a beautiful woman with massive breasts, thus showing that the expression of the Three-Headed Beauty was indeed a real thing. I have indeed learned something new."

"You're saying something very rude, you know?"

"I apologize. Then, may I ask why you feel offended? Perhaps, you prefer the term Ohdu2, which is rarely heard?"

"No, what is Ohdu even…"

"If I make a deduction based on the case of using a massive volume to describe the head, Ohdu can be inferred to mean the buttocks, or rather, one buttock. However, Lang Lang cannot understand. The buttocks of the Heavenly Flower Sword are even larger than the volume of a head."

"Ugh, what is this kind of woman."

Then, Qing suddenly cocked her head.

I'm pretty sure she was being beaten up with loud, thumping noises.

But considering that, she looks awfully fine, right?

"But are you alright? You're not hurt anywhere?"

"If you are asking whether there are any issues regarding sustaining life, physical disabilities, or difficulty in movement, then Lang Lang is fine. However, the pain is severe."

Hmm. She's a weird person.

For starters, she refers to herself by her own name, making me want to distance myself from her.

"Young Lady? Can you get up?"

"It is possible. However, this Lang Lang hopes to lay here for another hour, no, two hours."

"Ah. Okay. Then do so."

Qing looked around with a sour expression, and then, she looked at the young lady, who was lying flat on her back with a blank expression, yet her actions were absurdly sharp and precise, as she crawled on the floor.

I wonder where she was going? As she did so, she reached out her hand and pulled a crashed-down grilled pigeon to her chest, before tearing off a piece and chewing it.

She had no expression, so it was hard to tell if it was tasty or not, but from how her jaw was moving faster, it seemed she liked it.

Above her head, a number ‘one' was displayed in blue, lying on its side, as if it was a Chinese character, 一.

Righteous Karma, just one point.

She doesn't seem like a bad person.

Well, since she has the energy to grab food, she seems to be okay.