\chapter{Telepathy (12)}

The Blood Cult had secret techniques that were passed down for creating all sorts of monsters.

Blood Ghouls, Blood Devils, Blood Gu, Blood Demonic Humans, and so on.

In truth, when looking at the end result, they were all similar, having similar characteristics, but they were all different species that stemmed from different principles of creation.

If one asked why they created similar things through various methods, why they put so much effort into making monsters, or even if they spent their entire lives researching them, the answer would be this.

Yes.

Monsters were strong, easy to make, and could give the original lineage of the individual unmitigated grief.

Also, their security was thorough, with all sorts of restrictions or ways to completely remove the user's sense of reason.

For the dregs of the Blood Cult who only wished for the world to be ruined, what means could be more effective and secretive than these monsters?

As such, the history of the Blood Cult was practically the history of monsters.

Among them, Blood Ghoul was an abbreviation of Blood Devil, a monster that craved human hearts, blood, entrails, flesh, and so on, due to its endless gluttony.

Of course, a monster that only had high gluttony could not be controlled.

Therefore, they would repeat the Great Method to completely suppress their spirits, thus turning them into loyal dogs who would only wait for their master's single command of ‘Eat'.

People often imagine the completion of such monsters, that moment of completion, to be something incredibly magnificent.

They imagine something like a scene with blood and organs overflowing, blood fog rising eerily, and the sound of ominous bells jingling.

In the midst of all this, a very evil mage would roll their eyes back, scream, and go berserk before suddenly laughing maniacally and shouting, "Arise, my children!"

Then the monsters lying on the ground would open their eyelids in unison, revealing their animal-like eyes, flickering with an ominous glow…….

But in reality, the birth of evil was never that spectacular.

"Ugh, what is this? Is it spoiled?"

One of the youngest members of the Blood Moon Sect spat out what he had just put in his mouth.

"Ew, so gross. Why are you complaining about the food you eat, ugh, ew."

"See? I told you it was spoiled?"

"What's wrong with this? It's salty, bitter, and sour."

"Which bastard drank all the water?"

"I want to drink alcohol."

"Me too."

"Does anyone have alcohol? Ugh, why isn't there alcohol on our table?"

"Everything is spoiled… Oh. This one's… spoiled. Yes, it's truly spoiled."

"That bastard is still eating it."

"Woah, what's this? It's super delicious? This bastard was trying to eat it all by himself."

"What is this? Raw liver? Hey, I can't eat fishy things, but why does this look so delicious? Hey, give me a piece. Oh."

The youngest members were still quite young, from those just over their teens to those below their twenties.

Although they were relatively old for the new disciples of a sect, though.

Naturally, the dining hall was noisy with the bickering of youngsters their age.

"I'm hungry. I'm thirsty."

"Me too. I feel like I'm going to die."

"I wish I could have a drink, mmm. I wonder if they'll give us alcohol?"

"Are you even saying that out loud? All the older brothers are currently scattered throughout the sect."

"I never expected Big Brother to die. If I knew this would happen, I would've just gone to the Jin Clan Estate."

"Ha, how could we have known it would end up like this?"

"Don't say stupid things. How long would it take to become a Master if you were in the Jin Family Estate? Ten years? Twenty years? Tai Chi Fist? Ha, what Tai Chi Fist? Even my mom is a Tai Chi Fist Master."

"But the Jin Family Estate won't collapse even after ten or twenty years, right? Are we not going to collapse at this rate?"

"At the time, I thought that the Jin Family Estate would collapse."

They say mouths are the source of all evil, so birds hear words spoken in the day, rats hear words spoken at night, and Moyong Jun hears the words of the Moyong Clan, while the older brothers of the Blood Moon Sect heard the words of their younger brothers.

"What are you bastards doing! Is it time for a festival?! What's with all this partying?! What kind of mess is this!?"

"H-Huh. Brother Kalchi."

"Hey, all of you put your heads down. Jo Sam, you bastard, come out here."

"Yes, y-yes."

"You bastard, (slap) the one called the Great Senior Brother, (slap) when you should be keeping the mouths of these little punks shut, (slap) huh? I'm at a loss for words. What? (Slap) Collapse?"

Kalchi, an older brother who happened to be walking by, casually slapped Jo Sam's cheeks repeatedly.

If one were to ask if it was too harsh, it could be said that it was a just punishment for saying such things about the sect collapsing.

Even if that wasn't the case, the younger members of the Blood Moon Sect were always beaten up like this anyway.

After all, those who had grown so quickly after eating elixirs might turn around and bite them later, so they would have to make sure they established the hierarchy with their elders.

Although, they were usually eaten because they did things like that.

In truth, it was because the bastards wanted to bully someone given even the slightest reason, to suppress others with their own superiority, so the reason didn't matter.

Even with his cheek hurting, his ears ringing, and his body staggering, Jo Sam was extremely upset.

After all, he was all too aware that while his brothers couldn't even sleep properly at night because of thirst and hunger, these older bastards were smelling delicious, gorging themselves on good food, and acting out here.

The youngers had nothing but spoiled food on their table, yet these older bastards were acting like this?

Does that even make sense?

It was a known fact that people should never be made to feel resentful through food.

While one could say ‘it's not that big of a deal', people's food preferences were formed from childhood memories or traumas, so it was difficult to overcome them.

That was how significant eating was.

As such, when Jo Sam raised his fist, it was something that anyone among the older brothers who had been so talkative was due to experience anyway.

However, it could be said that Kalchi, having been on the receiving end of such an act from a junior, could feel that it was unfair for it to be him when others had been acting even worse.

But in the case that Jo Sam was tightly gripping his chopsticks, he should not feel wronged.

When eating, even dogs shouldn't be bothered, and those who bullied younger members while they were eating deserved to be stabbed with chopsticks.

"Huff, Brother! I'm sorry-"

"Gah! You, you bastard…!"

"I, it's not that, I just-"

Kalchi collapsed, clutching his shoulder.

Even if it was just two chopsticks, once they pierced through the shoulder, they would inflict a terrible pain, similar to a red-hot iron skewer.

It was when Kalchi was struggling to catch his breath while his body trembled that he suddenly felt a deep sense of dissonance.

What the hell. Why is it so quiet?

At that, Kalchi slowly lifted his head.

And there, he saw the younger members all looking at him, their mouths tightly shut.

For a moment, the sound of a loud gulp echoed loudly.

The sound of a gulp might be small, but when everyone gulped at once, it would be louder.

"Y-You, I told you to put your h-"

In front of the starving Blood Ghoul, human blood flowed.

The moment they smelled that bloody scent, the younger Blood Moon Sect disciples instinctively realized how to resolve that horrible thirst and hunger that was plaguing them.

And wasn't it the principle and virtue of the Unorthodox Faction to grow by killing and overthrowing their superiors?

The teachings they had heard and witnessed until now finally bore fruit, blossoming in full.

"Brother. Sorry, but… Just a bite… I'm begging you, just one bite."

"What? Argh!"

Kalchi screamed.

Because Jo Sam was suddenly biting his arm with a sharp grip.

Kalchi desperately punched, kicked, hit, and pushed Jo Sam away.

Jo Sam tumbled onto the floor, but blood spurted out from his arm, which had already had a chunk bitten out of it. The blood pulsed with his heartbeat.

"Y-You, you bastard! Gone crazy-"

Kalchi's words abruptly stopped.

Because all the younger disciples had rushed him at once.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Appearing here and there, like lightning, calling her mother like a child, it was Yeom Hwiyeong, who didn't have the qualifications of a ‘Hong', yet mysteriously showed his face from time to time.

"Hmm, what is this again? Where did you pick this up? You keep carelessly leaking your warm maternal love, so these half-baked things keep clinging to you. You can't bear to throw them away because your heart is so soft. But still, you should throw away dirty things like this, okay?"

"Just who is this softhearted person who keeps leaking maternal love? I don't think it's me, though?"

However, Yeom Hwiyeong was only looking at Qing.

Next to her, Gyeon Pohee nodded vigorously, showing his fervent agreement.

Qing frowned as she thought to herself.

What is this? Where is there a chivalrous person in Wulin who is as cold, detached, and merciless as me?

"Heavenly Flower Sword? Who is this rude human?"

Langlang, who had suddenly become ‘this thing', protested with a blank expression.

Qing paused for a moment, trying to decide how to introduce him.

"Ah, he's, uh, my adopted son."

"Hmm. That is quite surprising. Langlang is astonished. Heavenly Flower Sword, you have such a grown, unruly, and reckless child."

"But he's also a good son. Isn't that right, Mother?"

"Hmm. Though opinions on that may vary, it seems like that would be the common view, based on the present situation, wouldn't it?"

At that, Yeom Hwiyeong's nose pointed towards the sky.

What is Hee Mae even celebrating, clapping her hands like that?

Anyway, his Righteous Karma had increased again.

What is he doing running around that causes his Righteous Karma to increase?

But what is he doing wandering around at night?

Surely, that promiscuous brat isn't calling her ‘Mother' because she's a grandmother.

Well, if the two of them are happy, then it doesn't matter.

Then wouldn't it be a good thing?

I might as well just have her leave home and become a nun.

"The Heavenly Flower Sword's family history is quite intriguing, but that is separate from the fact that this human is very disrespectful towards Langlang."

"To me, your only value is staying by my mother's side. If you wish to amuse us, I won't stop you, but if not."

Yeom Hwiyeong's eyes turned icy.

Langlang also clenched her fists, seemingly unwilling to be pushed back, and assumed a martial arts posture, but then…

"Are you saying you wish to challenge me? Impertinent human. This Langlang wishes to resolve this through a conversation befitting a cultivated individual."

Upon witnessing the Sword Force that was clearly manifesting in the form of swords, Langlang immediately backed down.

"Conversation? What do you mean by conversation?"

"If you are a noble being of the Transcendent Realm, you have enough qualifications to be impertinent. This Langlang will gladly accept the impertinent attitude of the Heavenly Flower Sword's adopted son. That is all."

"Yes, that's how it should be."

Yeom Hwiyeong smiled fiercely.

Qing nodded her head as she watched this scene.

As expected, realm was the best.

I wish I could reach the Transcendent Realm too and make small swords that sparkle with my Sword Force.

"Well, though it's a bit concerning to keep her by Mother's side. She doesn't seem harmful. Anyway, Mother, I saw something interesting, you know?"

"Interesting? Is there a cooking competition or something? Or a grand opening? Or are they passing out discounts or whatever? Where is it? The food is always the best when they've just opened, after all."

"No, not something you eat."

"What is there in Guangzhou besides food that could be fun?"

"Langlang agrees with that sentiment. The joy of life is in food, and then, lying down and doing nothing. And the greatest joy of all is eating while lying down and doing nothing."

Originally, Guangzhou was a place known to be boring if one didn't care for fine dining.

"Hmm. I can understand why Mother has someone like you by her side. Never mind that. There were some odd guys, you know? Maybe Blood Ghouls or Blood Demonic Humans? Jiangshi? No, wait, now that I think about it, it can't be Jiangshi. Anyway, they were some bad people, I tell ya."

"Blood Ghoul? Blood Demonic Human?"

Upon seeing Qing's expression, Yeom Hwiyeong added a simple explanation.

"Ah. You see, Mother, your heart is soft, and your head is soft too. They're just monsters from the Blood Cult who eat people, Mother."

"Eh? The Blood Cult?"

"If there are such things in the Golden Treasure Gate, there are probably some in other places as well? And since Mother crushed the Guangzhou Vanguard, they must have been destroyed together. And isn't it likely that those Blood Moon Sect bastards also have it hidden away somewhere?"

"Hmm. The Blood Cult."

The Blood Cult. They were a group of truly evil and malicious scum, whom all the Orthodox, Unorthodox, and Demonic Factions detested.

Qing had already experienced them in Kaifeng, so they weren't just scum, but scum with abnormal sexual urges.

Come to think of it, the liquor bottles, I forgot about them.

It's been a while since I did some work.

Qing swallowed down the satisfaction that spread warm and sweetly throughout her, before quickly making a decision.

"Do you have any kind of evidence? I should tell Clan Lord Jin about this."

"They say this is a elixir that those guys eat? That the bastards of the Unorthodox Alliance sent it. But no matter how I look at it, it seems like the Blood Cult is involved."

Yeom Hwiyeong casually placed a pill on Qing's palm.

The pill was red and the smell was fishy, so no matter how you looked at it, it didn't seem like a normal item.

"Hmm. For now, I'll tell Clan Lord Jin about th-"

It was then.

-All personnel, prepare for combat! This is a real situation! Report back the number of personnel within a quarter of an hour!

-Prepare for combat! Real situation!

-Prepare for combat! Real situation!

Urgent voices from outside shouted to alarm them.