\chapter{Lineage (14)}

\textit{Is there a person that exists above the people?}

\textit{Well am I supposed to stand above the people?}

That was a voice that didn’t quite resonate with Qing.

It’s a blatant fact that the Emperor as the absolute supreme being who held the unmatched position in the Central Plain whether Qing agrees or not.

\textit{What’s the point of emphasizing that?}

\textit{It just sounds like 'I'm the highest so I'll do as I please'.}

But it seems like the Emperor wasn’t done talking yet.

``All men under heaven have dared to dream that they could rise above the Emperor. Those fantasies were something everyone has held. The Emperor stands above the people commanding with the majesty of one who rules the world.''

The Emperor continued speaking.

``However I am the Emperor chosen by Heaven and the reason they were not emperors lies in that very point. The people simply see the Emperor as their superior, someone who’s honored and respected above all. Is my word incorrect?''

``This girl will listen.''

``That listening of yours… The Emperor is the one who exists above the people. But is it only the Emperor who is above the people? Even the obscure local officials of villages, those lower-ranked officials can be said to be above the people within their jurisdictions. And isn’t Wulin World the same?''

In Wulin the Demonic Adepts receives more respect than other practitioners and the common folk fear and venerate them.

What about the local gentry represented by the Five Great Fmilies?

Even local officials deferred to the gentry who have long pretended to be local lords throughout history, enjoying their superiority above the common folk.

``Do you truly believe I wield more power than they are as their ruler? Am I truly the owner of the world and all its people?''

``Uh… Hmm.''

Qing fumbled with her words.

It didn’t seem right to agree.

If she said no wouldn’t that make her a rebel?

``Indeed. It was perfectly natural that Wutian wouldn’t recognize the command of the Emperor.''

The Emperor displayed a fierce smile.

``Is there ever a case where a person would give up their significant gain for a lesser one? Would a prime minister give up their position to take a minister role? Why would a person willingly move from a position of greater power to one of lesser power?''

If others had heard this they would be in shock.

The claim that Celestial Martial Emperor’s power surpassed that of the Emperor was a bold one.

Of course since Qing’s roots weren’t in the Central Plain she thought 'Hmm was that so? Even though he’s the Emperor?'

``Wutian had the freedom to wield all things in this world as he wanted. He was already the strongest and those who revered him would obey like loyal dogs or he would threaten them with his sword and if they disobeyed take their lives. For someone who could manipulate the entire world why would he care about the Emperor’s position?''

The Emperor shook his head.

``Look. I haven’t even been able to hold the Crown Prince’s wedding according to my will. It’s because those who aren’t family resist when I try to decide family matters. Is that all? I’ve lost my child and did not even realized it. They say that to govern a nation first one must cultivate themselves. But I haven’t even been able to hold my family together, let alone properly manage the nation.''

Suddenly the atmosphere grew tense.

In fact Qing was the very proof of the Emperor’s words. If the Emperor truly held powers akin to sovereignty, the imperial wedding would have already taken place.

But the reality was that after myriad opposition the Emperor had to lay out his intentions and seek understanding.

However the Emperor’s expression and tone were so calm that it hardly sounded like a complaint.

It was just a dry delivery of facts.

``So what then is this power of the Emperor that people speak of? Such power is but the imagination of dreamers and that is why they haven’t been chosen by Heaven.''

\textit{Didn’t the Emperor just say he was above the people a moment ago?}

\textit{It seemed that the position of the Emperor did carry some struggles.}

Qing recalled having lived as a beggar not even recognized among the beggars scavenging for rotten food discarded rice and insects.

\textit{Yet isn’t it enough just to be born into a good family and live well?}

``The Emperor is the one who exists above the people, someone who must exist. The people revere the Emperor as being in the Heaven but the Emperor is the one maintaining the existence of Heavenly Mandates.''

The Emperor looked at Qing and smiled bitterly.

It seemed Qing had no clue about what he meant.

``Have you read history books?''

The Emperor stated.

If the Emperor’s power were indeed so vast that he could wield anything as he pleased the world would be in despair.

Just like Qin Shi Huang, just like Wang Mang.

The people would come to hate one another and fight until parents exchanged their children to eat one another in a horrific hell.

The world was too expansive for one person to grasp; one person’s thoughts cannot reign supreme.

The world was too heavy for one individual to wield.

Thus they stumble around hammering at the earth.

``Also if the Emperor’s power was too weak then the world will also descend into chaos.''

When the Liu family dynasty fell into decline, the Emperor was too weak to steer things and allowed the treacherous ministers to go unchecked.

Those who cared for the nation wouldn’t fill their bellies with the Emperor’s authority causing all officials to turn into monsters that consumed the blood and flesh of the people.

Human nature was self-preservational so even the most gentle of people would rise up with a spear and become bandits in such times.

Above were the demons, below were the bandits; is there any difference between this world and hell?

``And if the Emperor does not exist, Zhongyuan will drown in blood and suffering.''

If there was no Emperor or if one cannot exist that was when the war begins.

The entire world would tear itself apart killing and bleeding endlessly.

What transpired at the end of the Liu dynasty was nothing short of chaos.

Even the leader of a gang who wove bamboo mats\footnote{Liu Bei} rose up to claim dominion over the world committing heinous slaughter in the name of a grand cause.

``Do you understand? This is our duty of the Heavenly Mandate. We must survive until the end and maintain existence. But we should neither covet power nor relinquish it. We shouldn’t lose what we have nor ought we to seek more.''

The Emperor wore a bitter smile.

``To simply breathe and exist, firmly seated in this highest place of the Forbidden City; that is my duty as the Emperor and the method through which I govern the world.''

Only then did Qing understand the Emperor’s words.

The Emperor exists above the people—not merely existing ‘above’ them but existing ‘as’ their very essence.

``Now you should understand why Wulin is a menace in this world.''

``Your Majesty however right now, Wulin’s martial artists wish for peace…''

``Do you not comprehend or do you simply not wish to understand? Then let me ask the Heavenly Blossom Sword rather than the Princess. Is there such thing as law in Wulin?''

``That is…''

Qing hesitated to finish her statement.

But how could she avoided the pressing question?

There were no laws among martial artists.

And under the guise of their warrior stance, swordsmen speak through their swords and knife users speak through their knives.

In Wulin resolving conflicts through dialogue was seen as a coward’s shame, while facing off with swords risking lives was regarded as honorable.

‘Official Imposition of Non-Interference’ was just an excuse for the government not to meddle in the affairs of Wulin and for Wulin not to meddle in government's affairs.

After all that very statement was born from the notion that the national law and the customs of the Martial World differed.

``Wutian should not have acted in such a reckless manner.''

Even if the oppression by the government was indeed a serious matter, it was still true.

Even if it meant tearing down the Forbidden City and slaughtering palace servants, he should have at least respected the Emperor and conveyed his opinions carefully.

No matter how strong someone may be, no matter how unmatched they were in the world, they should have made it known that they were servants abiding by the law of the Emperor subjects following national law.

``Or he should have accepted the Emperor’s mandate and ascended to the throne. How could he so irresponsibly destroy the very center that binds the nation, break through the walls that protect against turmoil in the world, and leaving as he pleases?''

It would have been better if Celestial Martial Emperor had taken the throne.

Then it would set the precedent where a strong individual could rise above the Emperor and naturally the law of obeying and serving the strong would have established itself as national law.

But now that was impossible.

Even if another absolute master were to appear and intimidate the Emperor to seize the throne, Wulin would not acknowledge him.

Wutian had refused to become the Emperor.

Since Wutian leaving the throne without claiming the title, it had became a righteous act to rectify the government’s behavior.

If another Wutian were to rise and forcibly capture the Emperor’s position, it would only be deemed as a vile act for one’s own power.

And that would be akin to the justification of the past when warlords of the Cao, Liu and Sun families ignited flames across the world for power.

When Wutian had grasped the Emperor’s throat and stood atop Huanggu Hall, the very foundation of the world had begun to crack and collapse.

And by refusing to become Emperor, he barred any future exists when the world collapsed apart from war.

This was what Wutian had done.

``If you speak of the good people of Wulin, I will speak of the wicked. Moreover how long can your good intentions last? In a world consumed by chaos it only takes one Wutian to break it apart. Is there any guarantee that a power-seeking Wutian will not appear?''

The atrocities committed by the Imperial Palace flashed through Qing’s mind.

From the Emperor’s perspective it may have been the best course of action.

They were attempts to grasp a semblance of legitimacy through some distasteful schemes, but if he directly raised an army against Wulin, Zhongyuan would be fragmented resulting in a massacre.

It would be the initiation of a Zhongyuan-style World War (which essentially means Zhongyuan was the world).

Indeed Qing had informed Wulin Alliance of this matter.

Wulin Alliance had made it clear that if the government made a move they would not remain silent and had prepared for war.

\textit{Ah. That Celestial Martial Emperor…}

Suddenly the Emperor’s actions—neither right nor wrong just a number—caught Qing’s eye.

\textit{Ah, that could be it.}

\textit{By simply existing steadfastly the Emperor could be preventing calamities.}

\textit{The countless bloodshed resulting from the Emperor’s actions must be offset by the vast blood that would arise in the future.}

\textit{However what was evil remains evil.}

\textit{But since it prevents chaos in the world it cannot entirely be deemed a Evil Karma.}

\textit{In some ways it might even be seen as an act of good for the world.}

\textit{Yet these were terrible attempts that could never be considered righteous.}

So indeed.

Being neither good nor evil.

Although Qing did not clearly understand the effects such Karma of good and evil might have.

Alternatively perhaps as the one responsible for all beings the source of some evil deeds offset by some good deeds.

However the Emperor’s attitude and his tone suggested the need to erase Wulin.

\textit{If only there were signs of hatred or such it would be different.}

\textit{But the expression with which he stated that appeared more like a matter-of-fact devoid of any regret.}

``Now it seems you’ve come to understand.''

Despite Qing’s best efforts to maintain her expression it was immediately visible.

\textit{Why? Because the Emperor is the father of Yuansui?}

\textit{Yet how could it be that both the princess and me wear the same expression? The Empress had said that all acts and behaviors amounted to Yuansui.}

\textit{But how could that be? As if habits followed not memory but the flesh—}

In an instant Qing lost her train of thought.

A thunderous voice shook her back.

``Then as a member of the Heavenly Mandate, fulfill your duty. If the top young master of the Martial World personally issues a complaint, then you can simply deal with the rogue Evil sect instead of the Wulin. Once the sect falls the remaining issues should be easily resolved.''