\chapter{Lineage (3)}

It was an old man's earnest advice filled with anger and the same amount of will.

The prince had a very sour expression on his face.

``Ahem, um. I can’t go that far……''

``Your Majesty, I am a sinner who dares to mock the Emperor! Why do you hesitate to immediately condemn me to the extreme?''

"Well, um, yeah. You'll know anyway, so I'll tell you in advance. Heavenly Blossom Sword was my wife, ugh, the woman who will become my wife—"

Duke Fan Yue's expression becomes quite serious.

"Your Majesty, a woman's beauty is fleeting. I understand you may be dazzled by the dazzling beauty of that fake beauty, but time passes, fleeting like an arrow. Even the most beautiful woman in the world fades like a withered flower as time passes. If I may dare to say that you feel a deep affection for a woman based solely on her appearance—"

``A designation of love! What are you talking about!''

The prince shouted!

Then, I rub my arms and scream with goosebumps.

``Don’t say such nonsense!''

Seeing the prince yelling in return, this time Duke Fan Yue's expression turned sour.

No, why were you getting angry when you said you would bring it in yourself?

``Then why did you mention the Crown Princess?''

"Hmm, hmm. It's because His Majesty, while ruling the world, was concerned about the tyranny of those immoral and ignorant rascals, those thugs who call themselves martial artists. Yet, instead of cutting them with swords and shedding blood, he embraces them with virtue and love, showing mercy. Therefore, he will appoint the most famous woman in the martial arts world as his crown princess, and let all the people know that heaven's love embraces all people."

It sounds good, and at first glance, it seems like the royal family was extending a hand of reconciliation to the martial arts world, saying let's get along well.

However, there was no one among the officials working in the government who was unaware of the emperor's hatred for the martial arts world.

Because all the officials who were either clueless or lacked connections had disappeared.

Especially for Duke Fan Yue, who knew that a person in the palace could not practice martial arts carelessly, it was a word that made sense the moment he heard it.

I will take away the best review index in the martial arts world.

"Ah. But how could we dare to accept a criminal who has falsely claimed to be the grandson of heaven as the crown princess? If such a woman becomes the queen when you ascend to heaven, what will become of that reckless woman who now claims to be the grandson of heaven and holds power?"

Deungcheon means ascending to heaven, and refers to the crown prince ascending to the throne of the emperor.

The expression for succeeding to the throne was ‘bowi’ or ‘deunggung’, and ‘deungcheon’ was a word that only the crown prince could use.

``So, I sent someone to gather evidence of the fraud, but it didn’t work out. Ahem. What can I do? There were more than a few virtuous concubines in the palace.''

A chaste concubine.

In particular, among the women who were offered to the emperor for political gain in foreign countries, there were more than a few who grew old and died without ever seeing the emperor's face.

Heavenly Blossom Sword will also be locked away somewhere in the West Palace forever after the wedding ceremony.

The pharmacist stroked his beard for a long time, and he looked like he was fidgeting and not knowing what to do.

Is it really that serious that a treasonous pretender was ascending to the position of crown princess?

Soon, Duke Fan Yue finally opened his mouth.

"Well then, I will gather evidence of your impersonation. If I have clear evidence, then I will be able to punish that heinous sin."

But somehow the prince's attitude was lukewarm.

"No, the Emperor said he'd summon the Heavenly Sword soon, so even if he revealed it now, there's no way we could postpone the wedding anyway. We can just tuck it away in a corner out of sight…"

``Your Majesty, I am a traitor who has insulted the Emperor.''

``Well, if I even take one of the West Palaces, I’ll be exhausted. Why bother shedding blood?''

"Your Majesty, in times like these, you must be determined and demonstrate the majesty of Heaven. Do not be entangled in personal feelings."

The prince answers with a look of disapproval.

"If you can find clear evidence, if that's truly what Duke Fan Yue intends, then give it a try."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

``How have you been, Madame?''

It was Wei Ba-seon's face that had been shining for a long time.

Qing greeted him warmly and asked if he would like to come in and have a cup of tea.

But Wibasun shook his head.

``No, it’s time now.''

``What time is it? What, ah. By any chance?''

``Yes. It is time to meet the Emperor.''

``Oh, I guess the schedule was finally set.''

Finally!

It was a long wait.

I came here because the emperor said he would give me a reward, but he just locked me in the palace without saying a word.

Of course, the facilities, treatment, and food were better than any other guest house I had ever stayed at,

The facilities and treatment were of this standard, comparable to the best guest room in the Sulga Sanghoe.

Well, come to think of it, the VIP room at Seolga Sanghoe was truly amazing. How can it be on par with the Forbidden City?

Qing asks Jae-woo about the good news.

``So, when will I meet him?''

Wibasun smiled brightly and answered.

``Right now. Let's go.''

"Huh?"

"This is the usual way of doing things at the palace. His Majesty, with his busy state affairs, I can't guarantee you'll have the time again, can I?"

That sounded plausible.

But this was originally how the Forbidden City treated its envoys.

A surprise summon after an indefinite period of neglect.

So, on the way, she learned a bit about the etiquette, and fortunately, there weren't any difficult procedures that visitors had to go through.

And, the center of the Forbidden City, Huanggu Hall.

The Huanggu Hall was located in the center of the Forbidden City, where the government of the vast Zhongyuan was administered.

It was also the largest single building in Zhongyuan.

Twenty sheets left and right, eleven sheets wide.

And the sheer size of one building.

If we were to express this in the most scientific and economical unit system unique to the people, which would allow anyone from the Qing homeland to immediately estimate the exact area upon hearing it?

A whopping 720 pyeong of exclusive use area!

And its height was a whopping eleven jang.

It was the tallest structure in the Forbidden City, with a height similar to that of a twelve-story residential building in Qing Dynasty's hometown, and even higher than the walls of the Forbidden City.

Even so, this huge palace did not stand on the ground, but was placed on a huge marble slab three stories high.

The three-story foundation was a symbol of authority that only the emperor's building in the Zhongyuan can have.

That is, it was a shape in which a palace even larger than that was located on top of a high castle wall.

How pathetic must a human being be when he stands before this magnificent height, this gigantic miracle!

Especially for the primitive people of the ancient primitive civilization before the development of human civilization, when electronic communication technology had not yet appeared.

So what if the people and the barbarians from beyond the borders see this magnificent sight in the vast Huanggu Hall Square beyond the Huanggu Gate?

Indeed, one can naturally understand that the Emperor was the Son of Heaven and the immense authority of the lineage descended from Heaven.

Overwhelming!

It was the majesty of the heavens that weighs down on the soul.

So, what was the feeling that Qing felt when he crossed the Hwanggeuk Gate and came face to face with the wonder and grandeur of the greatest palace in the world?

\textit{Wow! Is that real gold on the roof?}

\textit{If there's that much gold, how much is it in total?}

Wing was not overwhelmed by buildings or anything like that.

Because Qing was not primitive people, and it was not difficult to see large structures in her hometown.

So it just feels like she's at a tourist attraction.

``Oh,'' Wibaseon says, looking up at the sparkling golden roof tiles (not gold) and trying to guess how much gold they are, and seeing Qing estimating the weight, Wibaseon smiles smugly for some reason.

Whatever the inside, the outward appearance was nothing different from the reaction of someone who was overwhelmed.

Then, Wibasun shouts loudly.

"The young hero Ximen Qing has ascended the stairs of heaven at the Emperor's call! You must express your gratitude to Heaven!"

``Hurrah! Hurrah! Hurrah! Hurrah! Hurrah! Hurrah! Hurrah! Hurrah! Hurrah! Hurrah!''

As we were told in advance, we shouted "Manse Samchang" three times, and then, as if they had been waiting, the music of the Zhongyuan began to play.

Musicians in elaborate costumes, sweating profusely, play flutes and other instruments on both sides, and on one platform, they beat drums and strike long, hanging metal objects to add to the sound.

It was a grand welcoming ceremony filled with the smell of sweat, held in the Huanggu Hall Square on this hot summer day, without even a single blade of grass, let alone a tree.

Next, Qing steps onto the left stone path among the three straight paths leading to Huanggu Hall.

The stone paths in the Forbidden City have different routes available depending on one's social status.

The central path paved with jade was a passageway that only the emperor himself can use, while the path on the right was a path that only the heavenly bloodline and companions can use.

And everything else must use the left path.

That's why it's so worn out here.

On either side of the stone tablet, the golden guards, clad in splendid gold robes, hold the Unwol-do sword and perform a ceremony of extraordinary skill without moving a muscle.

But I can't help it because it's so hot, and beads of sweat form on my chin and drip down.

It was clear that sweat was getting into their eyes, but they didn't even blink, which was a testament to their elite skills.

Finally, when we reach the high stairs in front of the Huanggu Hall, Wibaseon shouts again.

``Young hero Ximen Qing, pay your respects to the Heavenly Emperor!''

``Young hero Ximen Qing bow to the Heavenly Emperror!''

Bow down towards the Huanggu Hall from the bottom of the stairs.

And then climb the first step one more time.

Climb the second step and bow one last time before the third step.

Only after bowing three times can one finally climb all three platforms and stand in front of Huanggu Hall.

And also, according to the court etiquette, from this point on, you must walk with your head bowed and only the tips of your toes showing.

No, it's all sorts of things.

But originally, this was roughly the method by which those in power increased their authority.

Thanks to this, not only in the East but in all civilizations, it was a similar practice to ask permission even to dare to look at a noble person.

Qing walks cautiously, looking at her toes under the fluttering cotton.

The silk on the floor was so soft and fluffy that it feels like a luxury item, right?

Fortunately, a gold thread was drawn across the floor, marking the exact line where the sword should stop, so Qing stopped there and knelt down.

Within the range that could be clearly read due to the space occupied by the Awakening Divine Art, there were only a few Wibasun and guards, but it was not that they were unknown outside of that area, and their existence could be read at the level of a vague mass.

Why were so many people gathered in this vast and windy Daejeon?

And ahead of me, there will be another tall staircase, and on top of it, a large mass will be the Emperor and his throne.

\textit{Now, I finally feel like I am about to meet the Emperor of Zhongyuan.}

\textit{To be honest, I've had a good fortune so far.}

Even though it was a palace, it was a place where the Qing enjoyed luxury surrounded by three very enthusiastic followers.

Because he was a patient who had suffered a serious injury and had never even pretended to be seriously ill, and in fact, he had forgotten about it.

What kind of person was the emperor?

A mad hatred that seeks to destroy the martial arts world.

A ruthless person who tried to kill his own brother for him.

When his brothers rebelled to survive, he was a persistent and cruel man who went so far as to use fire to kill them, even if it meant causing suffering to tens of thousands of people.

As was clearly felt in the assassination rampage, the rulers who do not seem to regard the people as people, who only care about themselves, were the embodiment of ruthless and cowardly power…

Does that mean he was a proper monarch?

In a country where no one trusts the government, what kind of role does the ruler who heads the government play?

``Young hero Ximen Qing, raise your head.''

Qing swallowed his saliva.

Qing had seen many evil people.

It was a bloody number that grew as large as the number of those who died and suffered because of it.

That was why evil deeds were red.

Because the blood that was sprinkled and the tears that were shed were red.

So what would be the emperor's evil deeds?

\textit{If he's the most horrific villain I've ever seen, I-}

\textit{Hmm? It doesn't have anything to do with me, does it?}

It was a feeling that suddenly made her heart feel lighter.

\textit{So what if the emperor is a villain?}

\textit{What does it had to do with me?}

\textit{I don't have the chivalry to punish the greatest villain in the world, like Jing Ke who attacked Qin Shi Huang.}

\textit{Sure, looking at the prince's condition, it seems like he might make a good emperor, but what does that have to do with me?}

\textit{I just need to protect myself, my friends, and my loved ones.}

\textit{Slaying a villain is always just a hobby.}

\textit{It feels good when a bad guy dies, but why would I sacrifice my life for it? Wouldn't it be just me dying? It'd be a massacre.}

After that, it was a relief to relax.

\textit{Come to think of it, what.}

\textit{There's no need to worry about this, right?}

\textit{However, I am curious.}

\textit{How much splendid Evil Karma will there be?}

\textit{I might see a limit where the numbers stretch from side to side until they touch the wall, or go round and round and end at that limit.}

So, Qing slowly raises her head.

On the seven steps symbolizing the emperor.

A middle-aged man sits alone on a huge throne that could comfortably seat three people, but because of that, he looked rather shabby.

And on top of that head-

Qing's eyes widen.

A number she never imagined. 

\textit{Did I see things wrong?}

It was a number that didn't change even after she blinked and unconsciously raised her hand to rub her eyes.

Above the Emperor's head.

A notation for numbers not yet used in Zhongyuan.

\begin{quote}
	\textbf{0}
\end{quote}