\chapter{Lineage (10)}

The emperor was surprised.

That was also very surprising.

The identity of the Cheonhwa Sword was something I could never have imagined, and it's not surprising enough to make me raise my hands comically in surprise.

Isn't this just absurd nonsense that's hard to even say as a joke?

But the sound was still vivid in the ears of the Emperor.

In both the East and the West, there was no word in the world that refers to parents who have lost a child.

A husband or a wife who had lost her partner was called a widow and a child who had lost both parents was called an orphan, but there was no word to refer to parents who have lost their children.

Because it was such a tragic event that no one dare to put into words, it was inhuman to call parents who had lost their children by such words.

That's why there's a saying, 'cutting instestines' (斷腸), which conveys both comfort and sorrow.

In the past, a sailor captured a baby monkey and took it aboard a boat, intending to raise it himself. Seeing this, the mother monkey cried loudly and chased after the boat.

Startled, the sailor tried to return the baby monkey, but the rugged terrain of the Three Gorges of the Yangtze River prevented him from anchoring his boat. He was only able to return it after reaching a narrow estuary at the entrance to Sichuan.

However, the mother monkey who received her baby back died immediately, and when her stomach was cut open, her internal organs were completely torn to shreds. \footnote{A story from 'Shishuo Xinyu'/ 'A New Account of the Tales of the World' by Liu Yiqing}

So, the heartache of a mother who has lost her child was so heartbreaking that it feels like her insides were being torn apart, and the terrible sound of a mother who has lost her child was also said to be a funeral.

The Emperor heard just such a thing.

Even the world's greatest doctor would have shook his head and recommended a comfortable poison, so the Empress's cries, as she held her daughter, who was unconscious and on the verge of death, all day long, must have been the sound of her own heart breaking.

If the monks of the Cheonnyeo Temple had not appeared at that time, the empress might have also fallen ill and passed away.

Fortunately, the heavens were kind and saved Yuansui, and thanks to that, the empress was able to stop crying.

But was the sadness too great?

The Empress begins to show signs of madness.

He said that the magic was not magic and kept his distance, and he hated the monk of Cheonnyeo Temple like an enemy and yelled that he should behead him immediately.

Then, he suddenly started making a fuss about offering a Buddhist offering, so he readily agreed to go outside the palace and get some fresh air, thinking that it would make him feel better.

Even though the empress was originally not allowed to go out of the palace without permission.

The Empress regained her previous weapon, as if the Shaolin energy was indeed powerful.

But now, again?

``Empress. That is.''

The emperor was unable to continue speaking and closed his mouth.

But it seems the Empress had something to say.

"The Heavenly Blossom Sword is our daughter. A mother can recognize her child at a glance, even if others don't. It's a mother's divine power to recognize her own child, born from her own womb and raised by her own mother. She's my daughter."

The Emperor thought it was Lady Deokseong who had raised her, but he kept his mouth shut.

He didn't know what to say to the Empress, who was mad. Telling her that she was talking nonsense will only make things worse. What good will it do to logically refute her in the face of madness?

Then the Empress's eyes, not just her eyes, but her eyes, became extremely venomous.

"Yes, Your Majesty, you wouldn't know. You've always disliked that child! That child, who would always cower and watch your every move, you wouldn't feel pity for her. Instead, you'd yell at her, scold her, and hate her! So, even if a fake were to take her place, you wouldn't even realize it! Isn't that right!?"

``…….''

The Emperor silently endured the Empress's anger.

"That's why I didn't try to tell Your Majesty. Even if I did, you wouldn't understand, and even if you did, it wouldn't be good for Yuansui. I thought it would be better for her to live out there as she pleased."

After a long time, the Empress, who had been spitting out fire, catches her breath.

The Emperor, who had been silent all along, quietly opened his mouth.

``Haa. As the Empress said, I will first confirm whether the identity of Ximen Qing is indeed Yuansui.''

"A child who has no memory after being sick, how do you plan to confirm this? If you intend to force the witches of the Heavenly Women Temple to confess the truth, then they won't confess the truth since they will die anyway. Isn't that right, Your Majesty?"

"No, the Empress also knows the method very well. If Heavenly Blossom Sword had no memories in the first place, then the palace's magic, which occasionally recalls memories, no, no."

The emperor waves his hand.

``Do this. The Empress will have to see for herself whether it was true or not….''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

``Madam, how are you feeling? Did the medicine I prescribed help?''

At that, Qing gulped.

Even though I swallowed the elixir, it's hard to say that there's no improvement at all, and if there is, that damn wedding, the cruel destruction of dignity, will happen.

I can't do this or that between my conscience and my dignity.

``Umm, it’s still a bit early to say……''

"Is that so? In that case, I'll need to take a blood sample for a more detailed pulse diagnosis. Now, Madam, would you like to do it yourself?"

``Oh, is it necessary to draw blood?''

"Shouldn't this old man also report to the Emperor? If your health improved, its improved. If not, he's not. Even if I'm not sure, wouldn't it be better to report that I have taken blood and looking into it to save face?"

Qing's eyes rolled at him.

But no matter how much I try, there was no reason to refuse.

And since I'm going to lose anyway, I should give my blood and say it's different because I'm a martial artist.

I can't give blood, but even if I say I'm still in pain, it'll only make people suspicious. I think it's time to be more confident.

``I’ll do it myself.''

Qing received a small jade bottle and acupuncture needle from beyond the mosquito net on the bed.

Anyway, thanks to my strong body, even if I ask you to do it, I'll just make you lose strength.

And after a while, Qing pushed the jade bottle filled with blood out of the bed.

"However, since this was a matter of vital energy and internal injuries, I'm not sure what will come out of examining the blood. While the Qi meridian and blood vessels might look the same, they're also different…"

Qing didn't forget to prepare the excuse.

If I get a blood test and say, "You're healthy," I'm just suffering from an internal injury, not a disease, and that was the foundation for my insistence.

"As I said, even this old man needs to show that he's working diligently to remain attached to the palace. Um, is the Empress still taking the herbal medicine? Fortunately, the ingredients are non-toxic, so it's practically a safe tonic. It's truly a blessing. Isn't it?"

As expected from a doctor who can see through the body's condition by feeling the pulse, he would have quickly realized that this prescription should be called a tonic rather than a herbal medicine.

``Ahaha… That’s right. If you take the wrong medicine, it can be a big problem, so thank goodness.''

"Hmm. I guess there's nothing I can do. I'll double the amount and secretly give half to Lady Deokseong. Then, please take care of it."

\textit{Did you notice or not?}

\textit{It doesn't matter either way though.}

\textit{If he had noticed, he would have pretended not to know and let it slide, or else he would have just been trying to deliver medicine to the patient as a doctor.}

After the palace doctor left, Gabiya burst into the room with great energy.

"Madam!"

``Hmm. I’m a little tired today….''

Qing expressed his displeasure.

I've gotten a general understanding of directional massage, but I'd have to say that Gabiya was a terrible textbook for advanced courses.

If you just rub it roughly, it won't be able to do anything because it won't be able to do anything, so it will twist its body and shake its limbs and make a fuss.

Even though the direction method was not a massage method that touches the sensitive area forever.

However, in this situation, practice was no longer helpful to Qing.

However, Gabiya was of immense help to Aekyung's yoga practice.

Even the head of the Heavenly Women's Temple, who was either the lord or something, said that such a quick accomplishment was surprising.

So, it was Gabiya who was openly pushing for direction practice.

I couldn't stand it anymore, so I brought a tough cloth and tied my arms and legs to the mosquito net posts at the corners of the bed.

Gabi, you're so sloppy…

Well, if we want to hone our skills here, we'll have to use a more dull character.

Well, Gunyeong was quite dull, wasn't he?

He's always so sullen and expressionless. How long can he endure that? I have to see his pale expression suddenly distort and he gasp for breath with my own eyes.

``That’s not it. Hehe, Mama, you said you wanted to see the Cheonnyeo Temple event before, right?''

Gabiya interrupts Qing's thoughts.

It was an inquiry about attending the Cheonnyeo Temple event that Qing had asked about before.

What kind of manly thoughts am I having right now?

Qing was startled and quickly shakes off the thoughts that came to her mind, turning her attention to the Cheonnyeo Temple event.

When Gabiya attends the Cheonnyeo Temple event in the morning, there was a 50/50 chance that her evil karma will decrease.

What kind of event was it to accumulate good deeds, or was it some kind of volunteer work, or was there some kind of volunteer work done within the palace, or was there something about the nature of Aekyung Yoga that was just so shady…?

It was a question that only made me more curious.

``Oh, really?''

"Yes. You're attending the next event. And hehe, Mama? And that's beside the point."

Gaby lets out a suspicious laugh.

I was wondering why you took so long to bring me such good news.

"This time, His Majesty the Crown Prince will also be attending. Hehe, Ma'am, would you be interested in our King Yeongjong's secret art of seduction? I'll definitely capture His Majesty's heart!"

Gabiya sat down, holding her head.

Qing was surprised.

Ah, I made a terrible noise and my fist flew out without me realizing it.

``Okay. Hmm. Let’s observe next time.''

There was nothing good about meeting the prince.

ZGVPdDc2cnQxMFU0bVlrbnZITXlVcVBoOGFYbWZQRVBidWJQZFZpakt5OVU5SU9UZ0pZWm5TL0NXcFc3c1lmbQ

And looking at the progress so far, it seems like the prince might also be in a state of love for magic and causing trouble.

``Even if you say so, you have already been honored at an event hosted by the Heavenly King……''

"Huh. Who the hell was going to just put their name out there? I said I was just curious, not that I really wanted to participate."

Gaby was startled and stands up straight.

"No, no! You've misunderstood. How could a celestial maiden dare to sell Mama's name so carelessly? The Lord simply said that Mama's name was already among those people."

So, this was after Qing's name was already on the attendee list.

And Gabya was trying to use that to her advantage, to get credit for herself by saying, "I asked you to come and see me," in a cheeky and spiteful attempt.

``This is, they’re secretly trying to eat me.''

"The Heavenly Maiden was only loyal to Mama. Please understand my sincerity."

Gaby, who was completely hunched over, slowly crawled while looking around.

He pretends to be deadly, but his true nature was that of a coward, and he was a brazen troublemaker who keeps making sly attempts.

But, well, I'm not the superior.

If it weren't for Gabiya, I might have died of boredom, no joke. So, in a way, you could say she's my savior.

``Um. So when-''

"mama!"

Then, another palace maid suddenly burst in, cutting off Qing's words.

It was a surprising sight to see both of my exclusive concubines barging into my master's room as if it were their own home.

It would be shocking to others, but the current has been like this for a long time, and now that Gabiya has seen it, I too have started to secretly follow suit.

"Mama, did you hear the news? You're supposed to go out to a suspicious gathering of Indian barbarian bitches tomorrow! Oh my gosh, how could these damn bitches be, huh? There's one here too!"

``Mom, ugh, I always get bullied. I, I just want to be of help to you, Mom.''

``Hey, what was this? Where did you come from pretending to cry?''

``Oh, you’re going too far, really.''

Well, they're just two people who bicker all the time.

It's a picture of Gabiya getting beaten up unilaterally, but Madam Deokseong unconditionally takes Haeryu's side.

anyway.

The date of participation was something I had heard of.

But, what kind of event was this that the palace maids have to hear about the day before, and it's an imperial event at that.