\chapter{Lineage (6)}

Ximen Qing's true identity was Princess Yuansui! Surprise!

``Look at her, lady Jo. Are there two women in this world who would lie down on their mother and act so wantonly?''

Qing was being treated unfairly.

\textit{Who is the person who forced me to lie down and sleep on your knees and say such things?}

But Lady Cho gained great enlightenment.

Even if Mom forced me to lie down, isn't it just like my own living room, lying there without any discomfort?

And countless scenes from the past overlap so powerfully in that spread out form.

Lady Cho blinked.

``Are you really Princes Yuansui?''

``Haven't I told you many times before that I was suspicious of that woman disguised as a sorcerer? Later, when I offered  Buddhist rites, by the Buddha's great compassion and mercy, I was able to get my daughter back.''

\textit{Well, I thought that was what Your Majesty said because she was not feeling well at the time.}

\textit{I thought she had finally gotten your act together, since you recently stopped cursing the witches of Celestial Maiden Temple as fake priest.}

\textit{No, it's not that, but because she has found the real Princess Yuansui, she was actually sharpening her sword inside.}

Then, Lady Jo's heart began to pound.

Who was it that dared to insult the prostitute of the martial arts world who had seduced the crown prince without even knowing her place on behalf of the Empress Mama?

Lady Cho was carrying a bamboo basket.

"Your Highness, I have committed a mortal sin! I spoke without even knowing the reason. Oh my."

``Oh, it’s okay. It’s all because you’re thinking of Her Majesty…''

``Cut out my tongue and sew my mouth shut right now!''

``You’re being too extreme…''

"It's because I'm feeling uneasy. It would be better if Your Highness at least beat me. I'll fetch full armful of whips, so please beat me severely."

Qing was like, huh?

If the extreme punishment of cutting off the tongue and sewing up the mouth suddenly changes to beating with a stick, isn't that a bit of a difference?

What was the difference between life imprisonment and probation?

Then the Empress comes forward and stops Lady Jo.

"Stop it. You already know Yuansui's nature, so why are you doing that? What kind of person she is that she would harm you? My dear, does anything come to mind? It's Lady Cho, the lady who secretly brought snacks from Lady Deokseong. How could you hear her footsteps and not jump up?"

``Oh, I see…….''

\textit{What on earth was the princess doing?}

\textit{If you hear the footsteps of the person giving you the snack and jump up, that's not like a princess, but like a dog, a canine animal, isn't that what you do?}

"Oh my goodness, Princess Yuansui. You've grown up so beautifully, yet how come your facial expressions are still so ingrained in you…"

Lady Cho wiped her eyes.

Judging by everyone's reactions, it seems like Yuansui was a truly beloved person.

``So, now you understand why I am against the wedding?''

"Huh? What do you mean wedding? Oh, how absurd. How could something like this happen in this world? It can't be, how could something so absurd and bizarre happen in this great world…!"

Lady Cho stomped her feet.

"I've relieved myself of my great burden, but I can't seem to calm down. If I had only strengthened my opposition and taken a firmer stance, the Emperor would have given up on my stubborn, unrelenting stubbornness. At such a time, my heart was heavy, and I had to summon you. Oh, Yuansui. What should I do…?"

The Empress stroked Qing's head, making a pitiful sound.

\textit{So, this ridiculous reward, this forced marriage that makes my skin crawl just thinking about it, ugh, what the hell was this?}

\textit{Anyway, to stop this, the Empress must continue to send a signal that she was absolutely opposed, resolutely opposed, and extremely opposed.}

\textit{Honestly, I was wondering if there could be any more opposition than there was now.}

\textit{You have already clearly expressed your opposition, and even fainted.}

The problem was that the mother, shocked by her daughter's terminal diagnosis, immediately put everything aside and called for Qing.

\textit{…would that be a problem?}

\textit{When I came here earlier, I saw everyone looking at me, as if they were very proud of the humiliation I would experience when I got ere.}

\textit{Moreover, the attitude of Lady Cho was like treating me like a criminal.}

So, the court ladies' good-looking gaze was because, to anyone who sees it, it's like a daughter-in-law being called away by a scary mother-in-law.

Isn't it like the summoning of a combative chaebol's wife from a soap opera in her hometown?

\textit{Well then, there won't be a problem, right?}

Qing tells the story like this.

There was a minor commotion as the Empress's expression became fierce and Lady Cho knelt, but that was only for a moment.

Now that it was no longer someone else's problem but my own, Qing actively expresses his opinion.

``If it looks like that, why don’t you go a step further and make it really look like that?''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The next day, shocking news spread throughout the city.

It was the talk of the town, with all the palace maids gossiping, and it was also terrible news that made people shiver and tremble.

The young hero Ximen Qing was summoned by the Empress in the middle of the night and beaten with a cane five times!

A person from the Qing Dynasty might tilt their head and say, 'Hmm, was that right?'

Just five lashes, what on earth was so terrible and shocking about this?

But this was an underestimation of the vast scale of the continent, with the exception of the spirit and character of the Zhongyuan.

Five whips as they say in the Zhongyuan?

This does not mean that he was hit with only five blows.

It means that he kept getting hit until five of his whips broke!

In addition, whipping was a horrific and extremely cruel punishment for the women of the Forbidden City.

Moreover, it was a terrible punishment that not only caused pain but also destroyed the dignity of women and made their souls sick.

Because the whip hits the butt.

And if you get hit on the butt for doing something wrong, was it really a punishment to cover it up?

Of course, you have to hit the buttocks, and if you can't cover them with your top, you have to take it all off and beat them.

These types of beatings were usually done in front of everyone around them as if they were a good spectacle, and the pain and humiliation were both shocking and shocking.

The harsh military discipline of the palace maids of the Forbidden City was notorious for various things such as pinching, stabbing with needles, forcing work on them, feeding them rice in one bowl, and not letting them sleep.

But as the saying goes, simple was best, and this whipping was considered one of the most feared punishments of all.

So, after hearing this fact, Qingdo understood that it wasn't Lady Jo who had pardoned him on her own and dramatically reduced his sentence.

I thought, "It must have been a serious matter that you said you would bring a whole bunch of reeds," and cleared up the misunderstanding.

Anyway, while these rumors were spreading like wildfire, there was another shocking piece of news.

It was said that the Empress Dowager gave the young hero Ximen Qing a palace and told him to stay at Hambok Palace among the six palaces of the West.

He said that there was no need for morning greetings and that he should just look after the bed every night, while at the same time, the maids of Jangchung Palace would go around stirring up all the sedge from the Forbidden City.

Since Hambok Palace was located directly behind Jangchung Palace, it was as if they had declared that they would beat the king every night by placing it right next to him.

So even.

"I don't think I can endure that much and become a nobleman. No matter how much favor I receive, in this world."

"Wow, then you can rest assured. With your appearance, you wouldn't be a noble even if the world were turned upside down. Congratulations."

``Why does this bitch speak so sweetly? Does it mean she wants to die?''

It got to the point where public opinion sympathizing with Heavenly Blossom Sword even arose.

The Crown Princess was the dream and hope of all the palace maids, and the envy and hatred of Cheon Hwa-geom, an outsider who took her place, was no ordinary matter.

Even so, it was so terrible that people started to say it was pitiful.

And that night, the remains of five abandoned sledgehammers were discovered outside, and my fears that he might not do something like that became reality.

According to the maids of Jangchung Palace, the sound of being beaten all night was so chilling that they couldn't sleep because it gave them goosebumps.

That was the sound. Clap. Clap. Clap.

Even if you listen very quietly, you can hear a soft sound that penetrates the thick soundproofing of the palace.

No matter how quiet the night in the Zhongyuan is, if I can hear this much, my butt will burst, if not rot away.

The thought of it was so terrifying that it makes the palace maids lose their sleep.

And the reality was this.

Clap!! Clap!! Clap!!

Lady Cho swings her whip with force.

It wasn't something to do on a summer night, so I was drenched in sweat and panting.

``Oh, I can do it.''

"Oh, Lady Cho, I'll feel better if you put in this much effort. Okay. Ah."

``That’s right, huff, huff, Mama Yuansui. Since you’ve spoken so eloquently, huff, was it okay to feel at ease with this level of hardship? It’s a sin, huff, huff, that’s all.''

While Lady Cho was beating the poor floor.

``Mom, can I eat-''

``Oh.''

"iced coffee."

A round piece of watermelon fits perfectly into Qing's mouth.

Square, square, what a great delicacy was a cool watermelon eaten on a summer night.

Moreover, the palace's refrigeration system, managed by eunuchs trained in ice-crafting, makes fresh watermelons so sweet and delicious.

And in the Zhongyuan, watermelon was considered a luxury food, a very high-class fruit.

Crack!! Crack!! Crack!!!

"ruler."

``Oh, I tend to eat all the watermelon seeds.''

"You. Didn't your mother repeatedly tell you not to swallow the seeds of fruit, as they were harmful? Why didn't you listen? Now, ah. Don't eat the seeds, just spit them out."

"iced coffee."

Qing felt the touch of the Empress's palm pressed against his lips. Hmm, this atmosphere really isn't right. If this continues, it'll spread like it did during the previous Shinnyeomun.

But the current Qing has no veto power.

So, the watermelon seeds that inevitably pop out fall onto the stern hands of the Queen Mother.

"That's right. She's always found watermelon seeds so annoying. But how can she, even lying down, never hear a single thank you?"

``Huh, huh, haven’t you been like that before? Huh, the other day, you were lying down, and I fed you, huh, do you remember?''

How could I remember? No, what on earth was she doing, lying down and being served meals?

At first, she was a bit unpretentious and affectionate, unlike other princesses?

I thought she was the typical kind and spirited female protagonist from a soap opera, as depicted in such a painting.

The more you know, the more amazing it becomes.

Is this a human or a beast?

Well, rather than that.

Qing rolls her eyes.

I shouldn't keep getting caught up in this kind of affection.

I have to tell you that I am not your daughter and I have no intention of living as one.

But in this atmosphere, I don't think I can even bring myself to say it.

After Jo Sanggung broke the stick five times, Qing escaped from the empress's arms, who seemed to be letting him go with regret, and went straight back to Hambok Palace through the back door.

Then, Gabiya, who had been waiting with her neck stretched out, fidgeting and pacing back and forth from the middle of the yard, rushes over and clings to me.

"Ugh, Mama, were you feeling alright? How about I apply the medicine right away? It'll help reduce the swelling and pain…"

``No, I’m fine.''

Well, what were you putting on a perfectly healthy butt?

``Madam Deokseong, Haeryu, and even Mama were suffering this humiliation, yet you don’t even pretend to step forward. I’m so worried about Mama that I can’t do anything, but everyone else acts as if it doesn’t matter. It’s just too much.''

Well, since both Lady Deokseong and Haeryu consider Qing to be a royal concubine, the only thing they want to do was spend some quality time with the Empress.

It's only Gabi who doesn't know that that's the problem.

"No, I'm fine. I'm a master, so even if I get hit with a sword, it'll only leave a scratch. But if I get hit with a cane, it doesn't matter whether I get hit five times or a hundred times."

``But, even so, how, how, ma’am. What can I do, my poor ma’am?''

Why do only unfortunate things happen to Gabiya?

The child was now unable to act fatally and was restless.

Anyway, if I continue to play the role of the daughter-in-law who gets beaten, I will be able to go home soon.

Of course, seeing this situation, he wouldn't be able to insist on taking her as the crown princess.

This discussion was originally supposed to be a reward for defeating the White Hand Witches, but if it were pushed through in this situation, wouldn't it be considered a punishment rather than a reward?

``I’m fine. Hmm. Let’s go to sleep now.''

``Wouldn’t it be okay if you went to sleep after the fairy looked after your wounds? Yes?''

Qing grabs Gabiya's shoulder and leads her into the main room, reassuring her.

"I'm fine. Well, then, the palace doctor was coming to take your pulse tomorrow, right? Then I'll ask if I can take more shots."

``What do you mean, ‘Is it okay to be right?’…''

It was a sound that didn't reassure me at all.
