\chapter{Lineage (11)}

The next day, right after breakfast, I found out I had been summoned by Empress Mama.

The Empress usually didn’t call for anyone in the mornings but perhaps she was going to the Cheonnyeonsa event today.

After all didn’t Gabiya say it was a royal affair?

And sure enough

``Have you heard the news? I’m sorry for the sudden announcement. Your participation was decided in haste.''

``Why would Mama have anything to be sorry about?''

At that the Empress smiled.

But wait? What’s up with that smile?

With a slight furrow of her brow and an awkward grin it resembled the kind of expression Qing’s friends would say looks straight out of a printed page.

Curious about that ambiguous smile Qing cautiously asked

``Is there something you need me to do?''

``I didn’t want to take you to such a horrendous event. I’m worried you might be shocked. If it’s too much to bear just keep your eyes shut.''

The Empress hesitated her voice filled with concern.

Hmm. With those words…

Could it be? Really?

Are we talking about a wild eye-popping exhibition by the ladies practicing the raunchy yoga of the Aekyeongnyeong-gae (Kama-Sutra-Tantra) something absolutely not suitable for minors?

Well I want to see it. How could I miss out on this?

Qing pounded her chest with a thump no more like a splash.

``Don’t worry. How old do you think I am? I won’t be shocked by something like that. I’ve seen all sorts of things in the Central Plain.''

``Still haah…''

The Empress sighed deeply.

Qing glanced warily at her.

``Um just to be clear we’re only going to watch right? No participation or anything? I mean I thought it was an imperial event…''

``Don’t speak such dreadful words.''

At that Qing felt a huge sense of relief.

While the spectacle might be interesting yeah I wouldn’t mind being with a beautiful woman instead of just pervy guys especially since Gabiya would be there too.

Let’s not think about the Empress…

So off to the Hall of the Celestial Maidens.

The Empress’s expression seemed uneasy her brow wrinkles refusing to smooth out but Qing was actually feeling a little no a lot excited.

And thus the Hall of the Celestial Maidens.

Hidden floors in the main building.

And heading down the stairs—

``Empress Mama was here!''

Suddenly a voice resembling Jeomsoi albeit much more sultry rang out causing an inexplicable wave of discomfort to wash over me.

This was the voice of a eunuch from the imperial concubine’s court emphasizing femininity to ensure their own safety.

Next came a sight of countless kneeling figures their crowns and backs to the floor.

``Oh.''

Qing glanced around.

What was this feeling?

It’s like coming back home?

The vast underground area featured marble bricks a rarity in Central Plain architecture.

But with the entrance being what it was the marbles were cut small and fastened. It sort of resembled the kitchens bathrooms or upscale restaurants back in my hometown.

Not simple white jade but marble— the same kind from Qing’s hometown the finest interior material even in the Central Plain.

And over yonder were the small platforms?

Or were they bathtubs?

From a distance it looked like there were shapes carved into them might someone be lying in those?

Five such indiscernible structures.

While I had no clue what they were for Qing swallowed hard.

What’s this? Could it be a full-fledged yoga performance?

Following the Empress Qing found a spot to sit at the back of the observation bench stacked against the stairs.

As everyone lay quietly holding their breaths it felt so tense that even breathing seemed muffled.

What in the world was going on here?

``His Majesty the Emperor has arrived!''

This time a different eunuch stepped in his voice booming with dignity unlike before.

Ah they were preparing to welcome the Emperor.

Since we’re still in some feudal-like primitive era was it? or was it a similar scene back in my hometown whenever a high-ranking official visited?

As Qing lay down quietly next to the Empress I felt those four legs of the space glide by.

Given my spatial awareness isn’t that the Emperor entering with a chair?

Long live! Long live! Long live! After three cheers.

Then the prostrating figures carefully lifted their upper bodies straightening their backs to kneel.

Why such an atmosphere…?

For folks who came to watch an exotic performance they looked way too tense.

After all who could comfortably watch a show with the Emperor right behind them?

While I was pondering that suddenly from the opposite side the shapes in the bathtubs? Platforms? Women emerged out of nowhere.

Even from the observation bench which was just two steps higher I hadn’t noticed the women who were lying down behind the platforms earlier.

They wore bold traditional outfits adorned with plenty of gold and silver accents on top while unfortunately they wore long skirts below draping a translucent blue fabric over their shoulders.

Among them I could spot Gabiya.

And in the very center stood a woman.

With a red jewel affixed firmly to her forehead she was a stunning beauty in the Central Plain style.

She looked somewhat Western but with those big eyes that seemed like they’d pop out if you tapped the back of her head and with heavily applied makeup she was absolutely enchanting.

Dressed in twice as many extravagant jewels as the other women she clearly presented herself as the ringleader.

That must be Asiya the leader of the Hall of the Celestial Maidens as Gabiya would say.

She glanced over at us but her gaze seemed a bit unfocused probably seeking permission from the Emperor.

And then the eunuch’s commanding voice echoed through the white underground chamber.

``They say to begin!''

The five at the front jumped to their feet.

Dressed in resplendent golden garments the elite warriors of the Golden Guard stood.

With their bodies turned the Golden Guards set themselves towards the platform and crashed to the ground slamming their foreheads elbows and knees into the earth with the most respectful greeting of the Central Plain—five body prostrations.

Long live! BANG! Long live! BANG! Long live! BANG!

As they crashed down heads planted into the ground bright red blood began to flow freely.

Then they plunged themselves into the holes shaped like people atop the platforms.

Next Asiya raised her voice.

``Now let the beasts in!''

The Empress jolted in surprise.

Qing was taken aback too.

Beasts?

I expected something scandalous but this?

No what was this now we’re on to something pornographic!

Moreover the ones in those bathtubs were all blokes!

Suddenly the Empress’s words popped back into my mind.

A truly horrendous event.

She’s worried I might be shocked.

If it’s unbearable I should just close my eyes.

Eek. I can’t watch this. I should keep my eyes shut.

Just as Qing made that resolution the left door of the platform swung open revealing the so-called beasts that Gabiya had mentioned.

Qing’s brows furrowed.

The beasts were human figures bound and muzzled tied to logs.

Following that the Hall of the Celestial Maidens’ women lifted the contraptions showcasing excessive strength that seemed disproportionate to their thin limbs.

Then they lowered down the iron chains and began to wind them around the contraptions creating a clanging noise.

Before long five figures hung upside down their heads towards the ground over the bathtubs.

It was at that moment.

The women from the Hall of the Celestial Maidens drew their daggers.

Qing was flustered.

Uh oh this has a peculiar vibe… What kind of sacrifice was this—

With a SLASH they sliced into the arms of the captured beasts.

Avoiding the rush of blood they made incisions that caused crimson moments to cascade down towards the helpless figures below.

Dripping soaking into the bodies lying below.

``Om Sarve Bhavantu Sukhinah Om Sarve Santu Niramayah…!''

Bring happiness to existence bring health to existence bring to existence a world where you can thrive…

Qing’s special skill—the simultaneous interpretation of foreign languages—recognized these as the prayers from the Zhongyuan.

Somehow they sounded similar to what A-mook-hap-rab used to chant but the serious tone of the monk’s Buddhist practices felt completely different from this.

More like the wicked charm of the seductress hissing like a snake and howling like the wind.

Asiya’s voice came through but it echoed as if six voices rose together.

Yet they were discordant creating a strangely unsettling dissonance for the listeners.

SWISH SWISH SWISH.

To the rhythm of Asiya’s chants the women of the Hall of the Celestial Maidens swung their daggers rapidly.

Blood flowed continuously from the gored beasts and the blood began to rise over the shapes of the humans below.

They then adjusted the height of the carcasses before plunging the knives deep into the abdomen—

What I thought would be a scandalous performance turned out to be a gruesome murder show…

But.

In a way I liked it.

Qing’s eyes sparkled with excitement.

To simply let the blood flow out through cuts which seemed mundane yet appeared to be a highly intricate job.

They were being careful to avoid splattering blood and to collect it neatly in the tubs below.

Moreover as they clutched the beasts from behind and penetrated their bellies it was painfully obvious they were making sure the innards didn’t spill out wow right on!

Qing realized Gabiya was quite the skilled slaughterer.

She understood why the evil deeds lessened after attending these events at the Hall of the Celestial Maidens.

Those being meticulously butchered were beasts not humans simply beasts.

Red as blood non-humans!

The events at the Hall of the Celestial Maidens were a form of execution for sinners.

But why go through such restraint? It was amusing but really.

The volume of blood from a human was substantial but not infinite.

Filling each bathtub takes the process of slaughtering ten beasts for each.

Since it seemed arduous at some point the woman holding the knife changed and Asiya herself just focused on shouting out Central Plain’s sinister incantation at the top of her lungs.

Before long the pools were overflowing.

The men lying in the bathtubs were completely submerged their mouths barely above the surface with only the straws they held peeking out.

``Sarvat Mangalam Bhavatu! Sarvat Kalyanam Bhavatu! Sarve Tjanaah Sukhino Bhavatu!''

Asiya’s incantation grew louder now resonating throughout the marble-white interiors of the underground echoing like thunder.

The priestesses of the Hall of the Celestial Maidens politely holding silver trays raised golden goblets and tossed them right into the bathtubs.

Hm? Am I imagining things?

Is the blood level decreasing?

It’s not my imagination.

The water level in the tubs began to slowly drop.

With the muzzled noses visible and the mouths from which the straws emerged the garments once lavish golden now clung to them losing their original vibrant shade as they soaked up the blood.

But briefly.

The blood-soaked clothing gradually lost its color.

``Oh…''

Qing could no longer hold back her exclamations.

What was this? A cleansing spell? Is it really possible to draw blood like that?

Though not very fast it was undeniably clear that the golden patterns in the drenched garments were spreading.

Of course it couldn’t be a laundry spell.

If such a magic existed sorcery would thrive in the Central Plain instead of being looked down upon.

Hmm so this was actually sucking up the blood?

Let it not be for consumption; let it be for the skin?

What sort of sorcery allows skin to absorb blood?

What even was this?

But Qing’s questions didn’t last long.

The Golden Guards now completely free of any blood suddenly stood tall with their arms wide spread.

At this moment the women of the Hall of the Celestial Maidens brandished massive hammers.

A moment from the past flashed in Qing’s mind.

That time back in Sichuan.

That annoyingly sturdy brat Elder Taesang used to swing a solid poison he had personally concocted hitting nothing but empty air.

Sure back then I was just some rookie a martial arts leftover but the intensity of his blows didn’t even have a scratch on me.

BANG! BANG!

The sound of giant hammering broke Qing’s train of thought.

The women of the Hall of the Celestial Maidens swung their hammers with all their might even as the Golden Guards stood firm shaking but refusing to fall.
