\chapter{Lineage (1)}

It was a human law that after losing three times in a row, one should admit defeat.

If it happened three times in the same way, it would be natural to doubt whether this person was human or not.

And here was someone who has lost three times.

"Your Majesty, it's the princess. The princess you so cherished and played with. The image of them laughing together, banging sticks together, was still vivid in my eyes. Can you not see it?"

"No, please. This. The guy you served was Yuansui, and oh, just how cunningly did he use his rhetoric to get you to believe him so completely?"

The prince sighed deeply.

And I didn't forget to add one more thing.

``And I swear to you, I have never spared you or played with you.''

The prince has not yet accepted the offer.

The Empress and the wet nurse had spoken, and now it was the close friend who had been by his side since he was walking around with a runny nose who was speaking.

Heavenly Blossom Sword was your younger brother.

However, the prince could not agree to it.

It would have been time to admit it after three times, but this was truly an inhumane, inhumane attitude.

But there was no problem.

Among the creatures of the Zhongyuan, there existed a race called the Sky, which was not human.

These were not humans, but gods who came down to earth for a short time to rule over humans as children of heaven.

So, it cannot be said that the prince's inhuman behavior was a fault.

I don't know if it's the conviction of the one who will rule the world in the future, or if it's an expression of some indescribable, immense rejection.

The prince sets out to find his side again.

To find someone who can deny the theory of the Heavenly Blossom Sword's magic, and someone with the authority to determine its true nature through countless experiences with magic.

And there was still one such person left.

Hwanggeukjeon Jang In-gi-do-wi, Beom Yak-gong!

If he was a master of the prayer team who had been in charge of Yuansui's escort since he started walking, then definitely.

So, Hwanggeukjeon.

``Are you saying that Heavenly Blossom Sword was impersonating Princess Yuansui?''

The Hwanggeukjeon craftsman, Beom Yakgong, had a very daunting expression.

Well, since His Majesty the Crown Prince came to see me in person, I welcomed him, but the things he said were so absurd.

"Your Majesty, Heavenly Blossom Sword was a martial artist of the highest caliber. He was also a child prodigy who was said to have reached the pinnacle of his power at the age of twenty."

"so?"

``If, as Your Majesty says, the Heavenly Lady, under the pretense of medical treatment, switched the noble body and claimed that Heavenly Blossom Sword was the real princess—''

``That’s not what Yeo-ga said! That con woman from Heavenly Blossom Sword was talking about pants!''

The prince jumped up and denied it.

He was a great drug addict.

"In any case, Your Majesty. The Zhongyuan were vast, and its people were more numerous than grains of sand. It may seem commonplace to speak of a state called "Transcendent." Even so, it's utterly impossible to rise from third-rate to the highest level in just a few years of cultivation."

The prince's expression brightens at that.

``Is that so? I guess that’s what it is.''

"Yes. A child born with unparalleled talent, who receives the Great Law from birth, cultivates the Eight Vessels, and cultivates fiercely for over twenty years from a young age, was still unable to reach the state of transcendence."

So, the fact that Heavenly Blossom Sword was a supreme martial artist alone does not mean she can't become the Princess of Yuansui.

It was clear evidence presented by one of the best masters of the Forbidden City.

"That's what the lady said! And yet, falling for that cunning woman's words, oh my— ahem, Lady Deokseong and Haeryu have already been deceived. It's truly frustrating. Even if Yuansui says she's grown up after her illness, how can that be proof that it's not true? Tsk."

``Lady Deokseong? Is that the current again?''

A wrinkle forms on Beom Yak-gong's forehead.

I wonder if there were any other people in the palace who were as friendly as they were at that time.

Even if you were a noble person, it was natural for you to be close to a nanny who was as close as your own mother and to a young lady who you grew up with.

Princess Yuansui was a very affectionate person, unlike other grandchildren, and she was definitely different from other grandchildren in that she never treated her servants like a master.

It was a friendship that even a mother and sister could not be this close, so why did the two come to such a conclusion?

``Come to think of it, I think I heard that the name of the Cheonhwa Sword was the Wolnyeo Sword.''

``Hmm? Is there a way to deceive people with the Moon Sword?''

``No, it’s not. I just thought of it.''

The pharmacist strokes his beard.

Moon Sword. Moon Sword… …. By any chance?

``Why, was there anything on your mind?''

"No. If that's true, then isn't he a sinner, unforgivable and deserving of human condemnation? How can I possibly help him?"

The prince subtly brings up the main topic.

"So, could Jang In-gi-do-wi take a look at the Heavenly Blossom Sword? I've been guarding Yeon-sul since he started walking around. I'm sure I can tell its authenticity at a glance."

Beom Yak-gong's eyebrows rise and fall sharply.

Well, isn't the prince's words strange?

In the first place, it was absurd for Heavenly Blossom Sword to claim that he was the real one while the princess was in the palace, but if that was the case, he should have been immediately arrested as a traitor who deserves the extreme punishment for the crime of contempt.

But instead of ordering me to chase him, you're telling me to check if it's real or not?

It seems likely that the Crown Prince was already inclined to accept the absurd claim that Heavenly Blossom Sword was the real Princess Yuansui.

What if? No way?

Beom Yak-gong slowly changes his attitude.

``Ahem. Then I will go and see her secretly.''

Even if he was the crown prince, he cannot arbitrarily transfer the affiliation of the Hwanggeukjeon's craftsman, Gidowi.

The Hwanggeukjeon Jang In-gi-do-wi was the person who commands the guards of the three most important halls and three corners of the Forbidden City, and was not he the Emperor's direct bodyguard?

So, even if it was the Crown Prince's order, you cannot leave your seat during working hours.

If he wanted to make time, he meant to make time after the officials had retired and the palace was empty, that is, after the evening when the moon had risen.

``Please take care of my request.''

The prince holds Beom Yakgong's hand tightly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing-i grumbled inside.

How long were you going to call people and then just leave them alone?

Even if he was the Son of Heaven, was this how he should act?

Calling a busy person, hey.

Could you at least let me see the Forbidden City?

Of course, there was a law for this.

The procedure for attending the emperor was a set of etiquettes stipulated by national law, so it was the custom of the palace to wait indefinitely in a state of confinement, not confinement, until one had shed worldly filth and purified one's body and mind.

This kind of infinite waiting and confinement was also a political tool that kills the opponent's spirit and wears them out.

Fortunately, I don't get bored because I have Gabiya, so I guess it's a blessing in disguise.

First of all, you can see Aekyung's various positions, which number as many as sixty-four.

And in the evening, a new routine was created: direction method, direction massage practice.

The reason the schedule changed from a direction method experience to a direction method practice was simple.

``Mom, would you like me to prepare some directions for you?''

"No, Mama. Why was that girl calling you 'Mama' so filthy? That filthy bitch—"

"No, I could act a little cute, with something like that. Hmm, but I don't think I need to prepare any direction from now on. I'm more of a Zhongyuan-style Chuna."

The pressure of the ocean current was just right, so throbbing. This was how a massage should be.

"See? This was exactly the eye level between you and me. How can a punk who hasn't even lived in a palace for a few years be so mean?"

``Ugh.''

Hae-ryu's nose rises and Gabi-ya grits her teeth in anger.

But that too for a moment.

"Well then, Mama, have you ever considered learning the directional method? I'm sure it'll be very useful later on."

Qing's ears perked up at that.

But the expression on the ocean current that stopped him.

``This. Where did you get the chance to use such a lewd method on Mama?''

"You call it obscene? Acupuncture was a health-promoting treatment developed over six thousand years. It's considered the most important tonic in Chinese medicine, raising body temperature and accelerating blood flow."

``Ugh.''

This time the currents were silent.

The direct maid of the royal family must be proficient in basic medical skills, so it was difficult to refute Gabya's words.

And from the beginning, Qing was interested.

It could be used as a last resort for a massage to relieve stress, or it could be a healthy massage that you could give to your friends by using a regular essential oil instead of the essential oils that contain the most effective ingredients.

In the evening, I was able to fill my time with participatory education, listening to Gabia's lecture on direction using ocean currents as a teaching material, and even practicing with Gabia herself.

After another day of meaningful and rewarding learning, Qing lay down on the bed, flanked by two court ladies who bickered with her dozens of times a day.

Although he didn't toss and turn in loneliness like before when he fell asleep alone, he felt more at ease or more reassured when someone was by his side.

Qing, who heard the sound of breathing from both sides, quickly drifted off to dreamland.

Suddenly, Qing's eyes widen.

Because of the huge presence felt from outside the building.

If I had to make a sound effect, it would be 'gooooo', and it was an ominous presence, like a thick black fog was falling.

Qing rolled his eyes and looked left and right.

Haeryu and Gabi were fast asleep.

He slips down silently, without making a sound, without the bed swaying, with the snake-like movements of a preparatory priest, so as not to break the silence, and picks up his clothes.

As I cautiously stepped out of the building, I noticed a figure standing proudly in the middle of the yard.

He has an ambiguous appearance, somewhere between middle age and old age, and was called an old man in his hometown of Qing.

However, his hair was pure white, neatly tied up with a round cloth, his mustache was long on both sides, and his beard was even longer between them, giving him a fresh-faced appearance.

But, the evil deeds were one hundred and seventy… …

Qing swallows his saliva.

A guy with a red number, and a guy who looked suspicious at first glance, came to me with a sword in the middle of the night, and, ma'am, he even stole my Moonlight Sword.

Of course, that was natural since weapons were not permitted in the Forbidden City.

Qing was on guard and observing his opponent.

The guy suddenly opens his mouth and asks.

``Would you like to know my convictions?''

``Uh… no? Do you need to find out?''

The visitor's expression becomes subtle.

"I am a shaman, and I was once entrusted with the protection of Princess Yuansui. Do you still not recognize me?"

The tense expression on his face softens slightly.

Somehow, I had a feeling it would be like this.

Since Princess Yuansui's old acquaintances came to visit one after another, I thought that after hearing Beom Gi-do's story, I would be able to see her face soon.

But, well, old relationships were relationships, and bad karma was also bad karma. How should we deal with this?

``I heard from Haeryu. Hey, hello?''

Qing nodded.

Beom Yak-gong's expression becomes more subtle.

``Are you, by any chance, Princess Yuansui?''

``Uh… no?''

Beom Yak-gong's eyebrows tremble greatly.

Although he claims not to be, his awkward expression was so overlapping that it looks exactly like someone else's at a glance.

``I heard that you claim to be the Princess Yuansui.''

"Ah. That's not what I said. Everyone says that, but, um, I don't know. I don't have any memories of my past, so… um. But, even so, I don't want to live as Princess Yuansui. I am just Ximen Qing of Jianghu, and I will always be."

Beom Yak-gong let out a heavy groan.

The prince claimed that Ximen Qing was deceiving people by pretending to be Princess Yuansui, but what she herself said was completely different.

furthermore.

"I've heard you're a master of the highest order. They say rumors aren't to be trusted. You're a master of harmony. If I hadn't seen it with my own eyes, I wouldn't have believed it."

"oh."

The fact that one can tell at a glance that the other person was a Hwagyeong meant that the other person was a greater master, someone who had reached a mysterious realm.

To be exact, I can't tell you exactly how far she's come, but even at first glance, you wouldn't think she's the young, bright-eyed Hyeon-gyeong.

Her heart sank.

Why didn't I think of that?

There could have been plenty of experts in the realm of the palace.

Didn't you know that the Zhongyuan was vast and there were many unknown masters there?

How could such a master not appear in the imperial palace, which possessed all kinds of wealth and divine skills from each sect?

The characteristics of blue were strong, weak, weak, strong.

I shrank down in front of the master of Hyeon-gyeong.

Despite that, Beom Yak-gong continued to ask questions with the same polite attitude.

``Could you please show the Yue Maiden Sword you have mastered?''

``Uh, why is that?''

``There’s something I need to confirm. Please.''

Beom Yak-gong draws his sword from his waist and lowers it into the air.

The expression "putting it down in the air" may sound strange, but this was the basic sword technique used by the masters of Hyeon-gyeong.

The sword with its handle extended forward floats up and slowly swims towards the blue.

Well, the swordsmanship isn't really useful in actual combat, so it's not until the early or middle stages of the game.

Qing took up the sword.

In fact, it was not a difficult question to figure out why you were being asked to unfold the Moon Sword, no matter how clueless you are.

As someone who taught it, I'd like to check whether it's real magic or not, but hmm. I wonder if I can just do it.

Martial arts were ultimately influenced by a person's habits, so wouldn't a teacher who has taught for a long time be able to recognize it easily?

But, that's the princess of the spell, and I'm the country.

Because Princess Yuansui's habits may not match mine.

But, if the master of the current situation tells you to kneel, you have to kneel.

There's nothing good to do right now.

Qing obediently unfolded the Yue Maiden Sword's Movements.

First Movement, Wolf-Child Pick Up a Branch.

Second Movement, No Longer Child, Playing With Monkeys.

Third Movement-

That was the moment.

"That's enough. I'm afraid someone might see, so please put down your sword."

Qing was startled when he sees Beom Yak-gong.

Although Beom Yak-gong was smiling brightly, his expression was somehow eerie.

Great joy, and great pleasure.

But something bothers me, a sense of discomfort.

Why? Is it because of my mood? Or was it because of bad karma?

No, that's not it, it's something, something that's vaguely familiar.

That was the moment.

Thud. The pharmacist drops to one knee and bows his head.

"Have you been well, Your Highness? My eyesight is clouded by old age, so forgive me for not recognizing you immediately."
