\chapter{Lineage (8)}

There was a rumor that there was a large library in the Forbidden City where all the martial arts from around the world were stored.

A treasure trove of martial arts, collected and perfected from all martial arts on earth and under the sky, when the power of the Imperial Palace was so great that it held the entire world in its grasp.

It was also said that the emperor ordered all sects to give it.

Or perhaps it was Admiral Zheng He, a great vassal, great general, great admiral, and a great explorer of ancient times, who collected all the martial arts of the land and went out to sea.

Of course, rumors were just rumors, and the palace has never said a word about this warehouse of martial arts.

However, for the people of Zhongyuan who could not live without martial arts, wasn't this truly a dreamlike place?

So, it was not important whether the Imperial Palace Martial Library existed or not, but it was a realm of faith that had to exist.

Because it was a place filled with dreams and hopes of one day entering there and learning a passage of Divine Art and becoming a world-renowned master.

However, humans were class-based animals.

From the first appearance of private property in the past to the distant future in Qing's homeland, didn't we form a thoroughgoing class society?

So, the dreams and hopes of those who have nothing were the daily lives of those who have nothing.

The same was also true for the Imperial Guard.

The visit to the Imperial Palace, which any person from Zhongyuan would long for, was nothing more than a daily routine for Duke Fan Yue.

It was a realm of work that goes beyond daily life.

Because the patrol of the Imperial Palace Martial Library was also his responsibility.

As he opened the door, the strong scent of books filled his nose.

Under the dim night light, the dimly lit library comes into view.

Night Pearl! A jewel that shines on its own!

This was the greatest mystery of the present Zhongyuan, a mysterious treasure whose principles no one can understood, a grace of Heaven itself.

But Duke Fan Yue was not particularly impressed.

No matter how precious something is, if you looked at it every day, you ended up not really feeling its value.

The same was true for the countless martial arts books of the Imperial Palace Martial Library.

No matter how many precious Divine Arts were just lying around, there were only a few martial arts that a person can master.

Just pick a good Qi Cultivation technique, learn a weapon technique that matches it, and learn one or two matching footwork techniques, and you're done.

You could learn other swordsmanship techniques if you wanted to, but wouldn't it be difficult to master even just one martial art in your lifetime?

Learning from many people didn't help much.

Even most of them had to learn martial arts on their own without a teacher, and it was just martial arts books.

Of course, the martial arts book of the Imperial Palace Martial Library has been made so that one can learn as much as possible on one's own, with detailed illustrations and annotated commentary in over ten volumes. However, the limitations of learning without a teacher were clear.

But what if you could fully understand the origins, meaning, and scope of martial arts without a teacher?

In that case, it would be advantageous to learn countless martial arts.

By mastering the group, comparing, separating, and combining them, you would be able to quickly reach the level of mastery.

The gaze of Duke Fan Yue turned to one side.

Under the mysterious green light of the night sky, looking forward but not looking forward, towards the distance.

It was a look that was unique to old people, a recollection of memories that traced back the past in that space.

'Wow, the smell of books. I love it.'

"Oh, you like the smell of books? I've never seen Your Highness read a book."

"Hehe, I just love the smell of books. But! From today on, it's different! I'm reading books too! I'm reading martial arts books! So, where's it?  Where is the real Yue Maiden Sword?"

'Ah, this way-'

"No! That's not fun! I'll find it."

The most desirable child in the palace, and therefore the most beloved troublemaker by all the palace people.

As was often the case with the daughter of an emperor, she was a nameless little monarch before she was given the title of princess.

Strictly speaking, she did have a name, but her real name was a precious name that only members of the Imperial Family could call, so she was simply called 'Your Highness' or 'Little Princess'.

The little monarch was busy going around the library.

'What is this? What…'

'That's a welcome sign, huh? Give it to me. No, people even brought this kind of junk into the library.'

'Hmm? Why? Is it precious?'

"That's, um, correct. It's a book that absolutely must not be damaged, so please put it back carefully."

'Yeah! Okay! Here!'

The obedient little monarch smiled brightly, and when she was told to put it back in its place, she handed the book on the Art of War to Duke Fan Yue.

Instead, return it.

She wandered around the palace for a long time, tilting this way and that, and even gave him problems to guess the letters she didn't know because she couldn't read them well.

And then eventually, something happened.

"Huh? There's something behind this book! Wow, someone must have hidden it! So, this is the Yue Maiden Sword?"

The best martial art for a young monarch was the Yue Maiden Sword written by A-Qing.

The hidden martial arts were the most precious martial arts, and the most precious martial arts were, of course, Yue Maiden Sword, so she had no doubt that the hidden book was the Yue Maiden Sword she had been looking for.

The young monarch randomly picked out books and putsit in Duke Fan Yue's arms.

King Duke Fan Yue watched with a pleased smile, thinking, 'Little Princess is being Little Princess again.'

However, even Duke Fan Yue frowned as she took out the book that was hidden inside the bookshelf like the upper stroke of the character 而, which was hidden in the place where the monarch had taken out so many books of martial arts.

What kind of person would dare to hide the martial arts book like that instead of properly placing it in a drawer?

Clearly, they were hiding it behind his back, planning to learn it by themselves discreetly, so if he got caught, Duke Fan Yue would be very angry.

That was the moment.

'Wow! Look at this! It's writing!'

'Huh? Your Highness!?'

It was the most bizarre sight Duke Fan Yue had ever witnessed in his long life.

Letters flow out of the book in the young monarch's hands.

It was an absurd and nonsensical expression, but wouldn't the characters actually poured out like a stream of water into the air and circle around the monarch?

Unlike the young monarch who was laughing happily, it was the moment when Duke Fan Yue was startled and reached out his hand.

All the letters rushed into the young monarch's body at once and melted, disappearing in an instant.

"Your Highness? Are you alright?"

"Huh? It's okay? What is this? Duke Fan, you're like a total wizard? So amazing! Can you do it one more time? Huh? Hurry up, huh?"

The young monarch only grumbled, thinking that Duke Fan Yue had shown her some wonderful skills.

All that's left was a single, empty book, with countless blank pages.

And after that.

The young monarch was urging the old man to do it again, jumping up and down and pulling at his robes, but when that didn't work, she lay down on the floor.

But then she quickly gave up and went back to find the real Secret Manual of the Yue Maiden Sword.

The next day, she claimed she had a dream where she saw Yue Maiden and was taught the real Yue Maiden Sword, and she shrugged her shoulders and her nose rose to the sky…

Duke Fan Yue's focus returned to normal.

The palace was no different from the past, the young monarch was gone, and all that remained was himself, who had grown significantly older than before.

At the Early-Stage Profound Realm, there was not much time left to enjoy life, so no matter how skilled you are, you cannot avoid time forever.

Of course, if you go to the next stage of profound Realm, that time can be greatly increased.

Duke Fan Yue took out a book from his bosom.

The title, written on a worn and tattered cover, was written in a sharp, flowing font.

無相庫.

The character '庫' means warehouse, so the title of the book would be Formless Warehouse.

It could be interpreted as a storage facility that holds martial arts.

Since then, Duke Fan Yue has tried his best to find out about this mysterious martial art.

At first it was for the young monarch.

It may seem harmless now, but who knows what problems it could cause later.

It could have been some kind of harmful spell or sorcery, so wouldn't it be possible to solve it secretly only by knowing the identity of the writing?

The problem of the Formless Warehouse had to be solved secretly.

Entering the Imperial Palace Martial Library without permission was a serious crime punishable by death, even if one was a member of the Imperial Family.

Rather, it becomes an even more serious crime because they were members of the Imperial Family.

It was not allowed for members of the Imperial Family, except for the Emperor, to learn martial arts. Even the Fairy Art, which was only effective for beauty, cannot be considered a martial art.

Fortunately, there were detailed records of the Wulin martial arts in the Forbidden City.

That was only natural.

Before Wutian era, they were considered a dangerous hunting dogs that could bite its master, and after that, they were considered the most dangerous enemies.

Wasn't it natural that you need to know well to prepare for danger?

However, the content was extensive and varied greatly depending on the region and time from which the rumors were collected.

Moreover, as the monarch's successor, Duke Fan Yue did not have much time to conduct investigations.

So quite a bit of time passed.

Duke Fan Yue was finally able to find records of a long-lost mysterious sect and the incredibly powerful divine arts they possessed.

Formless Art. Or more known as Minor Formless Art.

A mysterious martial art that allows you to instantly understand any martial art in the world and become a skilled master.

It was closer to a talent or special ability than a martial art, so if someone had heard such a rumor, they would have dismissed it as baseless nonsense.

But, what was the scenery that Duke Fan Yue saw?

If Minor Formless Art was the absorption of such letters, it would be a one-person martial art that only one person in an era can possess.

And if people knew the existence of such Divine Art, wouldn't they have fought to possess it?

Like that sect that was destroyed due to internal strife.

Duke Fan Yue carefully closed the empty book.

And then he just looked down.

To be exact, the hand placed on the cover, the back of the hand, the wrinkled skin with black spots growing on it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Hall of Conscience was the actual place where the Emperor conducted his affairs.

The Huanggu Hall was a place used only for large meetings or assemblies where all officials gathered, and the Yangsimjeon was where the emperor's business, mostly stamping his seal and granting permission for state affairs, was carried out.

And then, through that conscience, high-ranking officials of the Forbidden City enter one after another.

However, the high-ranking officials' expressions were a little uneasy.

When I came in at the Emperor's summons, I saw eunuchs and royal guards standing in a row on either side of the Emperor.

In particular, the expression of the Empress's younger brother, the Minister of War, was even worse.

This was because the military personnel of the Ministry of War faction, called Seo Chang, and the Ministry of War faction of the Royal Guards, that is, the Empress's faction, were not visible.

Of course, the Empress was the Emperor's greatest ally, so it was a faction that was tacitly permitted.

In fact, the Minister of War also secretly welcomes the strengthening of imperial power, but the Empress's intentions were so strong that it was difficult to do anything about it.

Since she was the most powerful decision maker in the current family, I had no choice but to agree with her.

However, no matter what, I couldn't help but worry that he was now going so far as to threaten me with force.

I couldn't figure out why he was doing this.

But that was only for a moment.

The Minister of War immediately understood the emperor.

"The reason I've summoned you at this hour was to clear up any misunderstandings between us and to sincerely seek your understanding. The reason I wish to send a lady to Ximen Qing is…"

The emperor has poured out his heart.

I hate martial arts.

And in order to keep the martial arts world in check, you have to give women to the martial arts world's women.

Jim promises that the new lady will not step out of the palace, and this can be put in writing.

Sincerity has the power to move people.

The act of honestly pouring out one's heart and revealing one's true feelings has an incredible power to resolve accumulated misunderstandings and bring about harmony.

So, what was the reaction of the subjects?

"How can Your Majesty promise us? It's beyond our power. Just give us your orders, and we will obey."

Dramatic conclusion!

That was only natural.

The subjects thought that the emperor was trying to increase the power of the imperial family by borrowing the power of the martial arts world.

So I lay down.

But what if that's not the case?

If it's something that's meant to drain and trample on the power of the martial arts world, then there's no reason to oppose it, right?

Besides, whether we were pro-royal factions or not (there was no anti-royal faction, that would be treason), aren't we all united as government officials?

And the enemy of the government was Wulin, and the enemy of the country was the barbarians.

It was not at all strange to gather strength to deal with Wulin.

However, the emperor was feeling a little bit absurd.

Those guys who were lying down and opposing, saying they would rather die, are now coming here and saying they will follow anything if they were just given orders.
