\chapter{Lineage (15)}

In fact, Qing was secretly thinking about something else during the conversation, so she wasn't really focused.

Because that's too big a story.

\textit{I mean come on—world peace hanging by a thread? That's a big deal for someone like me.}

\textit{What does the peace of the entire realm even have to do with someone like me?}

\textit{My roots are always in the foreign lands. I'm not even a barbarian; I might as well be an alien from another planet.}

\textit{Even living in Zhongyuan and getting used to its culture I'm realizing that the mindset of the people here was just fundamentally different from mine. }

\textit{So even when I'm with my precious friends in Zhongyuan I still feel this lingering loneliness—like I'm an outsider seeking warmth in a place where I don't belong.}

\textit{In that light the Emperor's opinions don't really matter to me whether he's right or wrong.}

\textit{I've never held any love for Zhongyuan so their peace feels like a distant tale.}

\textit{What matters most to me are the people I care about.}

\textit{Taking down villains is more of a personal joy for me. }

\textit{This might be a bit of an inappropriate thought, but if I had to pick a specific one, it's something like volunteer work: a sense of personal fulfillment? A sense of accomplishment? Joy? Something like that.}

\textit{That doesn't mean I run around slashing bad guys left and right while comforting those who've just met their end—absolutely not. }

\textit{I've never had that grand ideal to begin with; I'm just a simple person at heart.}

\textit{So even if the ruler explains the grand ideals behind governing the land I'm not interested in joining in let alone getting involved.}

\textit{Unless of course those ideals threaten my dear ones. Then that simply cannot stand. I won't allow it!}

If someone were to look into Qing's heart, they might call her an extremely selfish woman.

She were the type of people who have no interest in world peace, but also deny the methods of those who seek peace.

And yet, aren't they only concerned about the damage to their own people and worrying about how they can somehow avoid being left out?

\textit{But why should I be troubled about that?}

\textit{What's the big deal about world peace anyway?}

\textit{All I want was to quickly dispose of this status window, live closely with my Divine Maiden Sect members, have occasional outings with friends and savor the thrill of slaying villains.}

\textit{That's all I wish for in my simple dreams.}

So the Emperor's proposal was a bit—it caught my interest you know?

``Your Majesty, indeed that wicked and vile group of Unorthodox Sects must face proper punishment according to the national law. Their misdeeds have crossed the line, so if Your Majesty raise the flag for their subjugation, the people will gladly take up arms alongside you. They are indeed the enemies disrupting the peace of the world aren't they?''

The Emperor's expression turned odd.

It's probably because he was waiting for the martial artist named Ximen Qing to oppose his views.

``However, Wulin Alliance and the Orthodox factions are not the traitors you think them to be. They rather strive to maintain peace in Zhongyuan, and, to put it simply, assisting in the government's affairs.''

``Assisting in the government's affairs?''

``If a villain emerges among the masters of martial arts, they're quick as fine horses, running thousand of liss in a day. Of course they aren't a match for the Emperor's army. But they spill the blood of loyal warriors, so shouldn't the Orthodox Martial Alliance take care of those rogues first to ease the burden on the officials?''

``Your words are utterly absurd. How can that be condidered loyalty? It's simply a power struggle to protect their own interests isn't it?''

But Qing had already made up her mind.

Wipe out the Sapa folks and let the Orthodox live.

If she hadn't formed a solid stance maybe she wouldn't know how to argue. But once she set her mind to something, her tongue can weave words like they're poison threatening the world.

``Your Majesty, dare I say it hardworking farmers do not toil for the peace of the realm. Their efforts are to grow more and tastier grains to feed their families. It's all for personal gain isn't it? Yet because of their labor the fields were full and fewer people go hungry in the realm, isn't that beneficial on a larger scale?''

What Qing said would likely plagiarizing the opinions of the Westerner yet to be born in this era.\footnote{Adam Smith and the 'invisible hand' metaphor}

But it's not entirely true.

Because even from the perspective of current Zhongyuan there was a maste  of the Hundred Schools of Thought from two thousand years ago who shared similar views.

``How ridiculous—how dare you speak of Dao of the Shen family?''

This was the rebellious sentiment of the Legalists among the Hundreds of Schools of Thought, embodied by the likes of Shen Dao.

The teachings of the Legalist masters were straightforward.

Strong military! Strong laws!

Didn't follow the law? Then destroy them with the military!

But Shen Dao had another take immersed in the Taoist idea of 'let it be'.

The radical merging of Legalist and Daoist thought meant establishing strong laws but only limited the use of corrupt methods.

It directly targeted the instinctual connections (guanxi) ingrained in the people of Zhongyuan.

When that happens everyone would work within the law to succeed understanding that benefiting oneself under just law was also benefiting the world.

However Shen Dao's arguments were ignored by both the upper and lower echelons of society, he was not recognized as a great teacher. leaving him just one among the various masters.

That's because the corrupt actions of Zhongyuan people were like a primal instinct, the very reason for their existence.

To succeed in business one must rely on connections and bribes, use that to monopolizing markets and eliminating competition,  and collude among themselves to protect their wealth. Since there were plenty of people out there, isn't it natural to cut salaries?

The corrupt practices Shen Dao spoke of were precisely these dishonest methods, leading the people of the Zhongyuan to react in outrage.

How else would one become wealthy?

In a future that has not yet happened, the result was opposite of the Westerner, who was praised despite the same arguments.

``Shen Dao 's words only make sense when the military flourishes and the authority of the law is established. But I say this: your martial arts people already know the laws and disrespect them as if they don't exist. How can this benefit the state?''

But could Qing have not anticipated that reaction?

Qing had already memorized the teachings of the Hundreds of Schools.

It's a bit rote so it takes a while to recall, but once she gathered everything she needed, she could unleash the intangible poison that the Tang Family's Elder Taesang acknowledged.

``So if the Emperor's army sweeps away those heinous, Sapa the Orthodox Warriors will naturally kneel in reverence to that might.''

If they see the Sapa getting cleared out the Orthodox would have no choice but to follow the law wouldn't they?

If what Qing said was true, there will be great bloodshed in the world.

There wouldn't be quiet subjugation from the Sapa; countless soldiers would inevitably suffer casualties.

But what can you do?

Besides, afterward Wulin would fall under the royal authority.

\textit{So what? It's much better than getting wiped out!}

\textit{The Emperor seemed determined to clear out Wulin and I couldn't bear to witness our Wulin Alliance facing that fate.}

\textit{So let's throw the Sapa folks under the bus. The Orthodox will toe the line so spare them.}

\textit{And it is true that even for martial artists, it was somewhat problematic to draw one's sword and do whatever one wanted.}

\textit{But my hobbies might become a bit more difficult…}

The Emperor's expression turned strange.

``You want to sweep away the Sapa? If what you say was true then the Orthodox warriors mustn't participate to uphold the royal dignity?''

``However, if Your Majesty so commands it, Wulin Alliance will gladly lend its strength. However, the driving force must be the might of Imperial Military.''

``Half of your Wulin will burn. Does that mean the so-called Orthodox those who claim to be just will face threats as well? Can you guarantee that your Alliance won't resist?''

``If that's a concern then simply give me the order. I will certainly persuade the Alliance to understand Your Majesty's grand intentions. If I fail then you may enact what you originally intended.''

\textit{This is a promise I had to keep.}

The Emperor blinked in surprise. 

Although they looked very similar to each other, they were actually unaware of this.

Because it is difficult for a person to know his own appearance.

``Your words sound very sly. So your Wulin only extend to your Alliance where as long as they are safe everything else is fine?''

``If Wulin Alliance respects and follows national law, Your Majesty would treat them favorably. While there may be turmoil initially as the officials and martial users intermingle, eventually future generations will use their martial skills to benefit the country, leading to a more prosperous world.''

The current leaders of the Murim Alliance would not want to be under the rule of the imperial family.

But if the Imperial Court weren't oppressive and treated them well, when the time comes for the next generation to take over they might change their minds.

\textit{In short, treat the current Wulin Alliance well.}

\textit{And then let future generations do as they please.}

\textit{After all, they aren't my concern.}

\textit{As long as my Divine Maiden Sect, my friends and the current members of Wulin Alliance thrive, that's all that matters.}

\textit{Their future descendants can figure it out themselves.}

\textit{In fact they should be grateful to me for preventing the total annihilation of Wulin; let them fight for their own freedom.}

``Huh yeah. Ha ha!''

Suddenly the Emperor bursts out in laughter.

His hearty laughter reverberated throughout his vast residence.

``Yes, they said to forge great individuals, one must endure the harsh storms of the world. That's commendable indeed.''

\textit{Wait did he just compliment me out of nowhere?}

Qing was completely taken aback.

``Indeed, your suggestion of purging the evil from Wulin and taming the rest doesn't sound bad.''

``I'm honored, Your Majesty.''

Qing bowed her head in relief.

\textit{Looks like I dodged a bullet.}

Just as that realization hit her…

``However, before that.''

\textit{Uh oh. What now?}

``A representative of you Wulin Alliance must kneel before me and pledge loyalty. It doesn't matter if it's the leader of your Alliance, the Greatest Under Heaven you so admire, or someone with the greatest influence. If they come to me with unanimous consents to represent Wulin Alliance, I will bestow upon them the General's Sword.''

The General's Sword was a symbol of command. 

If it was given to the representative of Wulin Alliance, it would be an official declaration of Wulin Alliance as a military entity under the Emperor's command.

\textit{Hmm a representative…}

\textit{Could it be the leader? Or maybe Great Master Wunue?}

\textit{I thought it'd be a good idea to clear out the Sapa and gain recognition from the officials—but convincing either of those two seems tricky.}

\textit{What should I even say?}

She pondered her words, trying to recall the teachings and stories of sages.

But it's too early for her to start preparing for persuasion.

``But the representative of Wulin Alliance kneeling before the Emperor must be you.''

\textit{What? Me? Why me?}

``Ten years. I'm giving you ten years.''

``Huh?''

``You must seize control of Wulin Alliance by any means necessary and bow before me as its representative. If you do I shall grant you the permission of Wulin Alliance's survival.''

``Your Majesty—''

``You dared to discuss state affairs and suggested placing the Orthodox martial users beneath my authority, didn't you? Therefore as per your words I wish to bestow upon you the responsibility of guiding the Orthodox martial users.''

It suddenly occurred to me that both the Emperor and Empress have this habit of interrupting while only voicing their own opinions—it's a pretty shabby communication style that relies heavily on their authority.

You can't dare interrupt the Emperor or the Empress, because even if they interrupt others as much as they want, the listener has no way to protest.

``So, before that, shouldn't you prove your abilities first? So, put the Murim Alliance under your control and prove your abilities.''

``But—''

``Ten years. Stand before me with the Wulin Alliance within that time. You shall wield the General's Sword and confront the Samawaido. If not, I shall no longer concern myself with any pretexts. The world will witness what true power lies beyond the knowledge of your Wulin.''

\textit{Oh boy. What nonsense was this all of a sudden—}

As Qing's eyes started to tremble, a blue square suddenly appeared in her field of vision, as if to congratulate her on her achievement.

\begin{quote}
	[Bloodline Mission: Sell the Martial World]

[You have received a special order from the Emperor.]
\medskip

Actions required for mission fulfillment.

Bloodline: Sell the Martial World to the royal family for wealth and glory.
\end{quote}

Qing immediately swiped away the mission window.

\textit{No way what the heck is this bloodline mission? Seriously!}
