\chapter{Lineage (5)}

The Empress's fainting caused chaos, and the audience ceremony also ended up being left unfinished.

Well, the Empress was so shocked by the Crown Prince's marriage that she even collapsed, so it was an atmosphere where even the Emperor could no longer bring up the matter.

When the Empress opened her eyes, it was already midnight.

And the first thing she said when she opened her eyes was:

``Heavenly Blossom Sword, bring me Heavenly Blossom Sword. Now.''

Her attitude was so resolute that even the experienced old maids who served her mother gulped without realizing it.

Originally, it was a confinement, not a confinement.

Because he was preparing for an audience, no one dares to call him out first, and because he was staying deep in the crown prince's palace, no one can visit him without permission.

But now, after meeting the Emperor.

Of course, since it was still in a healing state, no one can visit it without permission, but it was possible to send someone to call it out.

So, the Empress's maid arrived at the hospital and said that the Empress was calling her.

``How was your mother?''

``That’s none of your concern. And do you have any right to be concerned?''

The old maid's voice was hoarse.

It was an expression of discomfort, asking, "How dare you ask?" and asking if he didn't know who caused his collapse.

Blue may be aggrieved.

Who asked you to be the crown princess?

Even if you beg for it, it was absolutely, absolutely, absolutely impossible.

This was the kind of sound that comes from calling a busy person and then suddenly taking out something that has been sitting there for a long time.

In fact, it could be said that he was the biggest victim in the current situation.

But Qing kept her mouth shut.

Miss, did you know that the Empress would be so shocked?

Still, I should have paid more attention.

I guess I should have just joked around a bit… … .

Only after the Empress collapsed did Qingdao Acha appear.

Of course, to Qing, she was just a mother who feels sorry and uncomfortable as a mother.

The Empress must have felt the same way when she suddenly heard the news of her daughter's death.

But wasn't it inevitable?

There was no way for Qing to contact the Empress, and even if he had tried, he would have had to send a message on the spot to inform her in advance.

But telepathy isn't some kind of superpower, like consciousness-to-consciousness or brainwave transmission.

It was a technique of transmitting sound to a single point by utilizing the inner energy, which was a cosmic mystery and pure energy, and was nothing more than directional sound wave emission.

Of course, he had to look at the Empress Mama, and his mouth had to move slightly. Someone would be able to figure out the circumstances of the transmission even if they didn't know the content.

Wouldn't the very fact that Heavenly Blossom Sword sent a message to the empress at that location be a huge problem?

Besides, if you're going to fake an illness, you have to fake it really badly, right?

In that situation, it didn't seem like a proper malingering would work,

At that moment, the palace maid's expression suddenly distorted as she watched Lady Deokseong gathering the lantern.

"Your Majesty said to see the Cheonhwa Sword, but she didn't allow those who flatter her to follow her. Lady Deokseong, why don't you just stay? I really don't understand why you've come all the way here, leaving Yeongsu Palace behind."

"Lady Cho, there seems to be some misunderstanding—"

"That's not the case, Lady Deokseong. I understand your affection for His Highness the Crown Prince, but shouldn't you have reprimanded her harshly? Instead, you're siding with His Highness and acting as a pawn in his schemes?"

``No, this person now.''

``Did I say something wrong?''

``No, that’s not it, oh my, oh my, oh my.''

Madam Deokseong clutched her chest.

The gaze of Lady Cho, who was watching the scene, was fierce and blazing.

``Lady Jo, no, that’s not it.''

``Ha, you rascal, how much grace has Her Majesty bestowed upon you? Yet, how dare you act like a swindler, acting like a swindler—something even a beast wouldn’t do.''

``No, that’s not it, oh, oh, oh my.''

Next to Lady Deokseong, Haeryu also beats his chest in the same posture.

I understand that Court Lady Jo was doing this out of concern for the Empress Dowager and that she hates the person who started this incident.

So, it's not like I should be upset or offended by being scolded.

That said, this person was the real Princess Yuansui, and the Empress was only trying to see her real daughter, and since she doesn't have a limited time, the Empress will soon shake it off and get up. It's something I can't just reveal.

So, I just had no choice but to be upset.

Meanwhile, Lady Cho's eyes were tingling.

Why, do you have something to say too?

No. Gaby closed her eyes quietly.

``Okay. Okay, let’s go.''

The palace maids and eunuchs surrounded him.

They didn't even hide their hostile expressions, so it almost looked like they were escorting some criminal.

Still, Qing's mood isn't bad.

Well, the Empress was very virtuous.

So, after leaving the Hill Defense Hall, exiting the main gate of Namsamso, passing the stone path on the left side of the main hall, passing through Bongseonjeon, and crossing the central road of Dongyukgung… …

\textit{Hmm. But isn't it a bit far?}

It's actually far.

Because from Namsamso's Hillbangjeon to Seoyukgung's Jangchungung, you have to walk about three li.

Besides, how could the palace ladies' gait be considered brisk? Rather, their strides were narrow, giving the impression of a brisk, busy pace. However, by the standards of the Zhongyuan, this pace was truly slow.

So the procession passes by so slowly.

In the dead of night, people were swarming around, lighting their lanterns, and in every palace they passed, there were many faces peeking out or standing out to watch.

It was easy to guess who the person in the middle, who was the Empress's maid, the court lady Jo, and who the large figure wearing a cotton robe and belt above and below the waist, like a criminal being transported, is.

As I looked, I saw that Mama had summoned the Cheonhwa Sword.

Could this really be a problem in the middle of the night?

It's not that it wasn't, but Lady Cho was walking more slowly on purpose.

Because the rumor spread throughout the palace, and you were to be completely embarrassed in the middle of the night.

How long did he walk, attracting the attention of all the palace ladies?

Finally, Jangchung Palace!

The maids of Jangchung Palace also came out as if they were watching something, each with their lights on, and as soon as they heard the invitation, hostile gazes poured in.

``Yiur Majesty, I have brought you Ximen Qing-''

-Let her in.

It was a sharp reply that came out before Lady Cho could even finish speaking.

Lady Cho was a little embarrassed.

Usually, in such cases, the Empress would pretend not to hear and Lady Cho would have to ask several times, and then she would make them wait for a long time with all sorts of excuses, making them kneel in the yard and humiliating them for a long time.

That was the proper order in which court ladies should discipline their subordinates.

The maids of Jangchung Palace were also looking forward to this sight, so they were positioned in such a stately manner.

But why did you tell me to come in right away like this, as if you had been waiting anxiously?

Even if the Crown Prince's business was urgent, please omit the shame and humiliation that should be given to such a brazen and lowly woman.

Lady Cho, just in case, once again.

``Yor Majesty. Ximen Qing-''

-Bring her in, hurry.

It was a dry reply that came back again.

The court lady gave him a look as if to say, "I know you're lucky," and then said, "What can I do? I have to listen to what you say."

So Qing carefully enters.

The Empress, whose lips were dry and swollen, seemed to have lost much of her energy after only half a day, and she struggled to get up after seeing Qing.

Seeing that makes me feel a thousand times more guilty.

In fact, it was a request I wanted to make very clear when I saw Her Majesty the Empress again.

I don't know if the owner of this body was Yuansui, but the current me was not Yuansui, but Ximen Qing, the flower of the martial arts world.

Just because they have the same body doesn't mean they can be a magician.

That won't do either.

Wouldn't the woman named Yuansui also be shedding tears of blood and cursing in the afterlife?

But how can I say such things in front of you now?

In fact, anyone who knows Qing would probably laugh at this.

Did the woman who thought like that sit on her knees and whine while eating the fruit that was given to her?

In any case, there was no one as easy to overcome as Qing in front of affection, so he was a person who would melt away and disarm on his own.

``Everyone, get out.''

"Your Majesty!"

``Come her. I have something to discuss with you alone.''

Then, Lady Cho gets angry.

"No! Your Majesty! Heavenly Blossom Sword is a martial artist, a commoner who exploits people without regard for superiors or inferiors, and an ignorant woman who draws her sword at the slightest hint of trouble! How can we allow Your Majesty to face such a brutal and vicious murderer alone?"

The Empress's eyebrows twitched.

"Absolutely not! At least, let me, even a small person, stand between us! If this vile bitch ever gets angry, let me stop her. Please…!"

The Empress's eyebrows twitched even more rapidly.

But the Empress soon let out a deep sigh.

\textit{What Lady Jo says comes from loyalty. I know that although she seems to be talking to me, she was also threatening Heavenly Blossom Sword.}

\textit{If you don't know the circumstances, it can't be helped…}

"Very well. Only Lady Cho remains, and everyone else leaves. This is an order. Quick."

The court ladies who were trying to follow the court lady, holding their breath, only swallowed air in vain.

So, only the Empress Dowager, the Empress, and the Court Lady Jo remained in the room.

"Come here. Let me see your face. I need to see what you look like. How seriously ill must you be? They say you won't live long. Alas, what fate has befallen me."

``Your Majesty, it’s dangerous-''

``Oh, Yujeong. It’s okay. Come on. Honey.''

``Um, Your Majesty. Before that, I have something to tell you—''

``Do you really want to come near me only after seeing this mother die? You are such a cruel child, why are you still sitting there with your face covered? You, huh?''

\textit{What else could I do?}

Qing approached the empress with a sly smile.

The Empress, who had personally uncovered the veil, held Qing's face, caressing and stroking it, tears welling up in her eyes.

"Poor thing, how can your face be so pale, so wounded? You're so beautiful, how can you be like this? I should have brought you into the palace a long time ago, but your wicked mother, out of a bitter desire for revenge, stalled by saying she'd punish the fake. If I had brought you into the palace sooner, you wouldn't have had to fight that vicious villain. Are you in a lot of pain? Are you not uncomfortable?"

``That’s right, Your Majesty.''

``Hey, why are you so stiff? Why don’t you come here and hug me? Oh, poor thing.''

``Excuse me. That’s-''

``Don’t say that. It’s freezing cold in this hot summer. You poor thing, my poor daughter. I’m sorry, I’m sorry. Yes, tell me honestly. How much, how much time do you have left…?''

``Well, Your Majesty, actually, I’m fine.''

"Hey, why are you trying to hide it? Your hands, your hands are like ice. Oh my, how can you be so frozen in this summer? Hey, hiding it isn't filial piety. Are you trying to make me a mother who loses her child twice without knowing anything? If you do that, I can't let you go alone. I'll go with you…"

This was the heartbreaking story of a mother with a terminally ill child.

\textit{Hmm.}

\textit{You still won't listen…}

Looking at Court Lady Cho, who was wide-eyed and had a blank expression on her face, not understanding what was going on.

Qing revealed the truth.

It's all just lies, lies.

Since the relationship between the Crown Prince and that, oh, that was so miserable that it was hard to even speak of it, she needed a strong excuse so the Emperor had no choice but to back down.

``Really?''

``Yes, it really is.''

``Really, really? Without a single lie?''

"Yes. I'm perfectly healthy, so you don't have to worry—"

``Haiyaa! This fool!''

``Ugh!''

Crack!!

The Empress' palm burned on Qing's back.

Of course, Qing's body was not so fragile that it could be damaged by the hand of a mere woman.

In fact, even if the Empress had struck with an iron hammer or a sharp blade instead of her palm, it would have only left a slight wound on the skin.

But, just because you don't get hurt doesn't mean you don't hurt.

\textit{It's not that I can't stand it, but, um, that's also, um, surprisingly, my back is very sturdy.}

\textit{Of course, if you were a master of Unrestrained Realm, you should be able to endure the pain of a mother's wrathful back slap, and even have the ability to fight back.}

\textit{But I can't just stand and be unaffected, and I definitely can't fight back.}

\textit{I should at least pretend to get hurt.}

Qing was making a big fuss, rubbing her back, pretending not to be able to reach the spot, and rolling around the room.

It was a crazy, desperate cry of pain.

And when Lady Cho saw that sight, her expression seemed to embody the very image of shock, and she muttered without realizing it.

"Princess……?"