\chapter{Lineage (4)}

Oh my. Oh my. Ugh. Oh my, tsk tsk.

As soon as Qing rubbed her eyes against the cotton thread, a background noise was heard from all directions at once.

Even if it wasn't in front of the emperor, it would be a bad look to rub your eyes in front of an adult.

Of course, Qing was in such shock that he couldn't hear.

Why zero (0)?

Can a person's karma be exactly zero?

He wasn't even born yet, and he's been doing the job of a guardian of balance by studying the exact lessons he learned at that age.

Before that, the villain, no?

The number of good and bad karma deeds was absolutely not a measure that can be used to judge a person.

Still, wouldn't it be a number that shows a certain degree of tendency, especially the older the subject, the more accurate the actions?

Looking at the track record so far, I thought the Zhongyuan evil deeds would hit a new high, or rather, a new historical low.

Why on earth?

Is this perhaps a special privilege of the Emperor?

Since it happens in the Zhongyuan anyway, if you add up all the good and bad deeds within it, you get a perfect spirit?

Qing rolls her head in confusion.

In the meantime, the emperor himself opens his mouth and gets to the main point.

"Listen, civil and military officials. Countless calamities have plagued Zhongyuan, but through the protection of Heaven, they have repeatedly been overcome. In the past, the evil Demonic Cult's uprising was like this, and the rebellious cliques of Jeong Nan and Jo Qin were defeated. And then there was Deng Wuqi's band of bandits… and the traitors Shin Ho and Chi Fan… But just as humans cannot defy Heaven, so too can these…"

The emperor recited the history of the rebellion in the Zhongyuan.

Until now, all sorts of people have dared to rebel against the government, but they have all been defeated.

"But even now, the embers of that treason lingered, and those remnants of traitors seek to undermine the peace of the world. They are none other than a group of beasts calling themselves the Blood Cult. Their atrocities are already reaching the heights… They practice cannibalism, incite discord and envy, fomenting war… They sacrifice people in nefarious rituals…"

Next, about the wickedness of the Blood Cult's rebels.

It was partly because the Blood Cult was not completely eradicated and was causing chaos by threatening to burn the world, but when evil deeds went too far, people blamed it on the Blood Cult.

The civil and military officials' expressions hardened at that.

It was never a good sign when the Emperor's words were long.

Because it seemed the Emperor wanted to give her a compliment that worth as long as the speech, and at this point, he was talking at an unusually long length.

And besides, isn't it still continuing?

If the introduction was this long, it wouldn't be strange if the Emperor decided to appoint her as a general.

``……At such a time, the people of Jianghu rose in courage and stood against the leader of the Blood Cult, known as the White Hand Witch. With the body of a mere woman, she achieved the feat of fatally wounding and defeating the wicked traitor. The courage and chivalry of a frail woman who charged against the enemy of Heaven are truly virtues worthy of emulation, and for this, I hereby bestow a great reward upon the young hero, Ximen Qing.''

The civil and military officials gulped at that.

'What on earth are you giving her?'

At the same time, Qing took a deep breath.

\textit{I didn't know what he would give me, but I felt like I had to raise my voice and unconditionally oppose the rewar that came after such a long-winded introduction.}

``Make Ximen Qing the Crown Princess, so that all people on earth and under heaven may worship and look up to this virtue.''

For a moment, silence fell over the hall.

Even the ministers who had been preparing to oppose, absolutely oppose, and absolutely oppose, just froze and stopped.

It was because they were shocked and dumbfounded by the absurd story that went beyond their imagination.

And a loud voice broke the silence.

``Your Majesty! What absurd words are you saying!''

It was the sharp cry of the Empress sitting on the phoenix throne on the right.

The officials who suddenly came to their senses let out the breath they had taken in at once with a huge roar.

``No way!!!''

``Please give me a full moon!!''

``Please keep your mouth shut and keep your mouth shut!!!''

It was a roar that shook the entire 720-pyeong Huanggu Hall, a truly gigantic battlefield.

\textit{Huh, what, what was it? What was it?}

Qing, who was pondering the Emperor's evil deeds, also came to her senses at the sight of this enormous force.

The Emperor's words were so long and boring that all she could see was the strange number zero. So, she can't help but keep wondering what it means.

So, she suddenly came to her senses as if the hotteok shop was on fire and people were shouting.

A subject suddenly takes a step forward from the left.

"Your Majesty! This is unacceptable! How could such a lowly woman be subjected to such a—oh, sob, such a miserable, unspeakable thing! How could you entrust such a lowly and despicable thing with such a weighty responsibility?"

All of a sudden, a swear word comes flying at her.

\textit{What? Something lowly and shabby? Suddenly?}

Then, one person from the right also took a step.

"That's right! Before deciding on such a crucial matter, we must first ensure that her conduct was clean and free from any impurities. What should we do if she were in a state of impurity, associating with countless men in Jianghu?"

\textit{Isn't that the kind of girl who doesn't know who she's been messing with?}

Qing's eyebrows twitched.

\textit{No, I think that's a bit harsh.}

``Even though she has achieved great things, she is still a woman of Wulin, Your Majesty! People of Wulin ware just thieves and barbarians who make a living by wielding swords and taking lives. How can you say such a thing?!

The tendons on her forehead flared.

She swore she had never killed any humans.

She only killed non-humans, and collected the appropriate price, the environmental beautification fee for cleaning up the world's pollution.

\textit{No, what's going on all of a sudden?}

\textit{Calling people over, surrounding me from all sides, and then taking turns cursing at me?}

\textit{Was this what you planned?}

\textit{Even if you hate Wulin, what on earth is this?}

That was the moment.

Along with the sound of teeth grinding, a gloomy voice that seemed to come from the depths of hell, a voice that made you think it might be from the devil of hell.

``Exciting. The water in your mouth was thick.''

This was the admiration of Empress Akmun.

It's not just the voice.

The Empress's expression was also amazing.

Her face was flushed red with blood, and countless veins were visible, while only the area around her chin, where her teeth were clenched, was pale and drained of blood.

Especially those terrifying eyes, if the concept of murderous intent were to be brought to reality, those were the kind of eyes it would look like.

The ministers, seeing the Empress's objections, were clearly in high spirits, and each and every one of them jumped forward and added a word.

"Look at that vulgar woman! It was said that women with large breasts were obscene, but what about that beastly figure? Even the Empress herself said (actually said) that one should not take in women with large breasts!"

The Empress's head suddenly turned.

Now, with a sinister expression on her face, she glared at the speaker, her mouth burning with flames.

As if she was determined to remember that bastard's face.

The subject who had been talking about the obscenity of the giant flesg was startled and-

``I’m so happy. I’m excited.''

And yet, he felt relieved by the agreement of this evil text that was leaking out, and instead smiled.

"Your Majesty, I also feel the same way."

The Empress thought about it.

\textit{I'll definitely take care of that bastard later. I'll take care of him myself.}

Then she looked down at Qing in surprise.

\textit{My baby, it's all for you. What if your tenderness was hurt? I want to run to you and hug you right now, but I'm glad you're hiding your face. If even the slightest hint of sadness had been on your face, how could I bear it?}

\textit{But it's all for your sake.}

\textit{Please forgive this cruel mother.}

The Empress regaining her composure and spoke further.

"Moreover, how could you possibly invite someone who doesn't even know etiquette into the palace? At a time when it's shocking to even dare touch her face in front of an elder, how could someone so impudent as to be unable to restrain herself while attending an audience with the Emperor be considered fit for such a position?"

Adadduk.

"Look at that height! A tall woman is naturally inclined to look down on everyone, so how could she possibly know respect? Isn't she clearly the epitome of a woman who would despise and trample on those below her?"

Crackle.

The Empress's teeth suffered greatly.

Meanwhile, Qing's stomach was starting to boil.

\textit{What? Even if you offer me a government position, I'll definitely refuse it, you know?}

\textit{But instead of getting an official position, I just get personal attacks?}

\textit{Should I reject this too and give them a nice beating?}

That was the moment.

"Enough. Enough. I wish to use this opportunity to encourage Wulin to respect the nation, unite, and be loyal. However, since you objected, I will grant her the title of Lady."

His subjects were surprised.

The law of negotiation: After making an unreasonable demand, pretend to yield and then get back to the main point.

If it was a demotion from Crown Princess to Lady, it would be a whopping three ranks lower, so it would be difficult to justifiably oppose it.

Besides, wasn't it all arranged for the prince to personally meet the Cheonhwa Sword and bring it into the healing battle?

Somehow, the prince didn't even say a word to the contrary and instead brought in someone.

However, Qing has not yet grasped the situation.

\textit{Granting the title of Lady?}

\textit{In Zhongyuan, did you have to get permission from the emperor to be called a lady?}

\textit{You call someone over, hold them for a few days, and then you say, "From now on, you're a lady," and that's it?}

\textit{So what is it like before that? Of course, I'm always a man, with no intention of becoming a lady like that.}

"Your Majesty! Didn't I tell you not to do so? How can you handle such a crucial matter of national importance, involving the Crown Prince's wedding, without any formalities? I simply cannot accept such a person as the Crown Prince's match!"

Only then did Qing started to understand.

\textit{What is this all of a sudden?}

\textit{The Prince's partner?}

The Empress's resolute opposition.

Thanks to this, the subjects got a reason to oppose.

"That's right! Your Majesty, no matter how illustrious this woman may be, we must first hold an examination and accept her according to imperial law!"

"The position of Crown Princess is vacant, yet he's taking a second wife before that! Even the common people would not commit such absurd acts, so how could the Imperial Family do so? The customs of the world are to be observed and accepted by the Emperor!"

Qing understood the situation accurately.

\textit{It's not that they gathered to curse me, but the Emperor tried to marry me off to the crown prince, so they came out in protest with all kinds of excuses.}

\textit{Somehow, the Empress was the one who said that.}

\textit{Yeah, good job. Oppose it. Oppose it more.}

The Heavenly Blossom Sword swearing contest continued, and the Empress's dental health continued to deteriorate rapidly.

"This was the Heaven's will for the nation! If the righteous one who defeats that Blood Cult ascends to the throne, all the people will emulate them and seek to subdue the evil cultists! Furthermore, Wulin will see the young hero and understand the Imperial Family's grace and the fairness with which it leads the world!"

The emperor exploded.

``How can you oppose this meaning with the superstition that a woman’s qualities are determined by outdated etiquette and appearance?''

His subordinates kept their mouths shut.

However, the way they were looking at each other was not at all agreeable, and it seemed like they were waiting for the right time to oppose again.

Even if that was true, it was not welcome news to the subjects.

Should they just watch as the Imperial Family gained more support from Wulin?

That was the time.

Qing carefully opened her mouth.

"Your Majesty, may I, a humble servant, granted permission to speak to Your Majesty?"

All eyes were on Qing.

``I permit it.''

``I don’t know how I can repay the kindness you have bestowed upon me.''

Then, a clear pronunciation that resonated clearly and was pleasing to the ears, and a beautiful voice that no instrument could match.

At that voice, the face of the empress, who was no different from a demon, suddenly showed a faint Buddha-like smile, but everyone was looking at Qing, so they didn't notice.

"Although this girl is ignorant, I believe that the most important virtue for such a weighty position is to be healthy and hold the position for a long time. If such Consort were to become frail and suffer an unfortunate fate, how tragic it would be…"

The faces of the subjects brightened.

'This was a symptom of malingering, a sign of malingering.'

'Yes, that's right, that's a good point.'

'If the Crown Princess were weak, it would be a huge problem, and if she were to die, it would mean that the Mandate of Heaven is no longer with the imperial family, and the authority of the Forbidden City itself would fall sharply.'

And Qing did not disappoint the subjects' expectations.

"However, this girl was seriously injured in the skirmish with the witch, and the meridians was marred. Even if I were to spend the rest of my days recuperating, it was uncertain how long I will live. Therefore, this girl wishes to retire and quietly recover her strength beneath the trees and mountains of her hometown. Please grant me permission."

``…Is that really true?''

``This girl’s condition was confirmed by the eunuch who guided me, who also felt my pulse.''

The emperor's head tilted at that.

Then, Wibaseon, the eunuch of the royal guard, who had been standing quietly on one side, bowed.

"The words of the young hero Ximen Qing are correct, Your Majesty. Based on my understanding, the terrible Qi known as the White Hand Witch's White Hand Poison has filled and overflowed her dantian. I have temporarily blocked it with the prescription of Sun Live Elixir, but her condition remains critical."

The emperor had a very suspicious expression on his face.

``Then, let’s have the palace physician look into the details-''

``Ah, no…!''

The emperor could not finish speaking.

It was because of the empress who suddenly lost consciousness and fell from her chair.

``Look here! Your Majesty!''

``What are you doing! Call the palace physician immediately! No, bring in the maid!''

``Your Majesty, I will serve you!''

In an instant, the room became a scene of chaos.