\chapter{Lineage (2)}

Qing was surprised and raised Duke Fan Yue up.

Since Qing was from a country that strictly adhered to Confucian customs, it was inevitable that she would feel uncomfortable when an old man knelt in front of her.

Of course, those with more than 100 points of Evil Karma could be treated as inhumane and made to kneel, gutted, and laughed while talking.

But in this case, not only was the other person showing favor, but they were also someone with whom her body have a connection from the past.

"Seeing your great accomplishments, Your Highness, I too am delighted and filled with immense pride. It was truly a pity that I cannot boast to the world that this old man taught you swordsmanship."

"Well, that's not even certain yet. Also, even if you were to look at my swordsmanship and feeling familiar with it, my swordsmanship has actually evolved several times."

At first, Qing's swordsmanship was nothing more than a rigid imitation of the martial arts that martial Art Window had directly engraved into her brain.

And it has evolved many times so far that now she could wield it freely with the imagery she want.

So, if he looked at Qing's technique, it wouldn't be the same as Yuansui's technique, so how could he be sure of it?

"How could I don't know that? But how could a master of Unrestrained Real cling to the bad habits of their early swordsmanship days? Such a person would never reach Peak Realm, let alone Unrestrained Realm."

"Then?"

"Didn't Your Highness unleash the true form of Yue Maiden Sword? There's only one person in this world capable of such skill: you."

Qing tilted her head at him.

There's only one in the world.

``Oh, not two?''

There must've been at least one other person who taught her, it's not like her ancestors suddenly appeared in her dreams and gave her martial arts.

But Duke Fan Yue shook his head.

"The Yue Maiden Sword that I taught you was a common martial art in the military. No matter how much Your Highness urged me, how could I dare to impart martial arts so carelessly? However, the Yue Maiden Sword is considered the most fundamental of the military's basics, and its form is one anyone can emulate, so I taught it to you."

No matter how much the princess cried, whined, begged and threatened him, a subject who lived off the palace's salary could not dare to break the law of the land.

But fortunately, the young Yuansui read the story of the Yue Maiden and became engrossed in the legend, requesting the Yue Maiden Sword.

Even if it were to be discovered, it could be overlooked by saying that she was just immitating the training of the Embroidered Guards.

And it actually worked.

It's not just one or two days that the young princess was so excited that she picked up a wooden sword and swung it around.

'Take this, Yue Maiden Sword, Yue Maiden Ascension, Yue Maiden Chongcheon, Yue Maiden Gwangcheon!'

For some reason, she created names that started with Yue Maiden and ended with Heaven and shouted it out. There must be thousands of eyes and ears that witnessed that all over the palace.

But everyone thought,'Princess Yuansui is being Princess Yuansui again', and passed it over without thinking much about it.

Even some of the royal guards and eunuchs collapsed with a loud 'Kwaaak' reaction, satisfying the young princess.

Then some guy made careless comments.

That bastard identity was never found.

'That's not the real Yue Maiden Sword, it's a fake Yue Maiden Sword.'

'There is a real Yue Maiden Sword.'

'Although the original copy is kept deep in the palace's secret chamber, it was a legendary sword technique that no one has mastered until now.'

Children were creatures who overestimate themselves.

She was a creature with the baseless belief that she could do what others could not, so Yuansui couldn't help but be amazed by this revelation.

The original secret manual was deep within the palace!

Something no one has mastered until now!

Legendary swordsmanship!

It's not a lie.

Clearly, there was a copy of the original manual.

However, in a time when martial arts did not exist, it was a Secret Manual that only showed a few postures in pictures without a single word about how to use its Inner Qi.

It was also drawn by a painter who doesn't know swordsmanship, so it's just a series of scenes without any context, without any consideration for basic postures, movements of the sword and body, or the flow of the movement.

It was nothing more than a picture book, a painting that showed that the ancient Yue Maiden and A-Qing were beauties.

So, of course, no one could master it.

The true form of the Yue Maiden Sword remained only as a legend.

``Huh? So shouldn't Princess Yuansui has nothing to do with my Yue Maiden Sword?''

"No. Your Highness learned it. From that tattered picture book."

It was an absurd story.

``Huh? How?''

``In your exact words, ‘Because I am the very essence of A-Qing! I am a peerless genius!’''

``Was she really a genius?''

"I don't know. From then on, it wasn't just a simple imitation of swordsmanship. It was a serious matter punishable by execution under state law, so I reported it to the Empress. After receiving a severe reprimand, you stopped training and only wielded it as a form of play."

Hmm.

That didn't mean she didn't swung it at all.

\textit{I really want to see with my own eyes what kind of princess she is.}

``But, aren’t Your Highness also known as the successor to the Shaolin's art of Tathagata's Divine Palm, which was said to have been lost?''

``Uh…It just kinda end up that way?''

"In fact, I've always wondered, too. What kind of accomplishments would you have achieved if you had truly studied martial arts? What if you were truly a peerless genius? Perhaps you possessed some uncanny ability to grasp the entirety of a Secret Manual. What do you think?"

``Hey, where would you find such ability?''

Qing (a martial arts skills thief with just a slight contact, habitual offender) waved her hand.

Duke Fan Yue carefully examined her expression and then answered firmly.

``Such an ability exists.''

``Huh? Really? Has anyone ever done that? Maybe the Elder Celestial Martial Emperor, a Spirit, or something like that?''

``It's Your Highness. Not Wutian\footnote{He dropped the Emperor part}.''

``Yes. It must've been Celestial Martial Emperor.''

"It's not Wutian. Come to think of it, I've also heard rumors that you inherited Wutian's martial arts skills."

Duke Fan Yue's eyes narrowed.

``Your Highness, by any chance, do you know of a martial art called Formless Art\footnote{无相功; 'Wuxianggong'}? Um, no.''

Duke Fan Yue changed his words halfway through.

Because he could tell without even hearing the answer by looking at that expression, that blank expression that appears when you really don't know anything.

But Qing became curious.

``Formless Art?''

In the past, there was a mysterious sect with unknown masters.

The martial arts of that mysterious sect were all divine arts that transcended the world and possessed extraordinary abilities.

At first, as befitting a mysterious sect, they lived a life of isolation from the secular world, but gradually they came down to the world and began to enjoy being admired for their ever-changing divine skills.

As a result, they were so arrogant that they called themselves immortals and dared to claim to be above heaven.

This was something the palace cannot leave alone.

It was at the time when the palace were preparing to punish them severely.

Suddenly, they started fighting among themselves, fighting over who would become the master of martial arts, and then one day they were reduced to ashes.

Because of that, those mysterious martial arts skills also ended up being scattered to different places.

``Oh, I think I’ve heard that somewhere…''

"It's a famous anecdote. It's also proof that no matter how powerful the so-called martial artists may be, they ultimately cannot escape the limitations of greedy barbarians. Those who dare to claim to be impersonators of the heavenly realm, like immortals, have fought in greed and fallen, leading to their downfall. It's only natural for the martial artists to suffer this fate."

Suddenly, the atmosphere was filled with hatred for Wulin.

\textit{Why bother meddling or denying it? Just keep my mouth shut.}

``The Formless Art was also their divine skill.''

Formless Art without trace, or Xiao Wuxianggong\footnote{小无相功; Minor Formless Skill; from Jin Yong's 'Demi Gods and Semi-Devils'}.

Those who have mastered Minor Formless Art would be able to understand all martial arts in the world just by looking at them.

Furthermore, when you learned a martial art that you have understood, the achievement will transcended decades and you will immediately became proficient in it.

Even if you learned conflicting martial arts at the same time, there were no side effects.

It was a supernatural ability that would allow you to skillfully handle all the martial arts in the world as if they were your own.

"Oh…"

Qing was impressed.

\textit{That martial art sounds just like Martial Arts Window.}

\textit{No, isn't that something that beyond Martial Arts Window?}

\textit{The Martial Arts Window could only register marial art by touching the complete manual or hearing the complete Sutra, but if you just look at it and understand it, you can master it with your body at a level that takes decades of training.}

\textit{This guy, Martial Arts Window, acted like it is so great, but it's just an ordinary thing. Really sloppy.}

The Martial Arts Window would be very frustrated if it knew Qing's thought.

'This ungrateful bitch doesn't even know because of who she's still alive and well.'

But since there was no other way to protest, it can only feel wronged. Of course, the Martial Arts Window who didn't have its own will didn't even know that it was wronged.

"But is that really true? I don't quite understand it. What do you have to learn to achieve that? Is it some kind of miraculous study method?"

Weren't the 100-day study method for the CSAT, the 50-day study method, the 30-day study method, and the study method before the CSAT no different from the empty dreams and hopes of those who haven't put in the effort in the past?

"That's just the story that's been passed down, but unlike other Divine Arts, its true nature hasn't been clearly revealed. It could be a sacred object, engraved into the soul through some form of sorcery rather than learning, or it could simply be rumor. Besides Minor Formless Art, other martial arts have occasionally surfaced even after their lineage's demise, such as White Rainbow Palm Power\footnote{白虹掌力; Baihong Zhangli}, Six Yang Palm\footnote{六陽掌; Liuyang Zhang}, and Subtle Wave Treading Steps. Ah, you're the current owner of Subtle Wave Treading Steps, right?"\footnote{Including Minor Formless Art, they're all martial arts from Jin Yong's 'Demi-Gods and Semi-Devils'}

``Ah! That’s right. That’s it!''

``Oh, do you remember something?''

"No, I thought I'd heard that story somewhere. The person who gave me the Subtle Wave Treading Steps Secret Manual told me about it, saying it was a blood-curdling Secret Manual, and that they fought fiercely. Right?"

``Didn’t I already tell you that they killed each other and the sect was destroyed…''

The tone of Duke Fan Yue's answer seemed somehow gloomy.

"Ahem, Your Highness. I'm just so touched to see you grown up like this."

``Oh, you want to go in?''

``I sincerely wish to be by your side as I have been in the past, but please forgive me for not being able to leave for long due to my duties as the Huanggu Hall Commander.''

``No, why are you apologizing?''

At that, Duke Fan Yue smiled brightly.

"Come to think of it, those days were truly wonderful. Still, I'll visit you often. Will you grant me your permission?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The prince was waiting without sleeping.

\textit{What if even the Duke Fan Yue falls for that Heavenly Blossom Sword, that evil impostor's deceitful maw?}

\textit{If everyone who has been close to me since childhood all agrees and claims that the Heavenly Blossom Sword was the real Yuansui…}

\textit{What can I do?}

\textit{At that time, there was no choice but to step forward and negotiate.}

\textit{Even if you can fool others, you can't fool me.}

Even just looking at past records, it's like that.

Even though countless palace officials were fooled by Yuansui's excessive cheerfulness and disgustingly polite pretense, didn't the crown prince himself see through Yuansui's true nature as an uncivilized beast no different from a pig or a monkey?

\textit{So, let'ss strip away the abominable hypocrisy of the Heavenly Blossom Sword and expose the beastly nature hidden within it. Then, everyone will know the true nature of that fake Yuansui.}

\textit{No, what the heck. If this were the case, wouldn't it be like the Heavenly Blossom Sword was hiding its magic?}

\textit{Where did the accident start to get into a maze?}

\textit{Indeed, the Heavenly Sword, how it bewitches even the heart of a woman! How terrifying its true nature!}

That was the moment.

-Your Highness, this is Duke Fan Yue.

``Oh, come in.''

The prince welcomed guests in the middle of the night.

Since the Crown Prince's Palace, Namsamso, was connected in order from the southern gate to Dangyeongjeon, Danbongung, and Hilbangjeon, naturally, to enter and exit Hilbangjeon, you must pass through Danbongung.

So, the path that Duke Fan Yue takes after stopping by the Healbangjeon and seeing the Qing was very natural and free of unnecessary details, and he goes to the Crown Prince's quarters.

``So, how was it?''

Then, suddenly, all of a sudden, it was Duke Fan Yue kneeling before the prince.

``Your Highness, please punish me.''

``No, this person. What are you doing?''

``I see a traitor who dares to impersonate Tianchao\footnote{天朝}, and yet I did not immediately punish her, but returned empty-handed. This sin is so great that it pierces the heavens.''

The term 'Tianchao' referred to the dynasty of heaven, that is, Zhongyuan's Imperial Family.

And if you say that she was a traitor who has insulted the Heavenly Empire, wasn't that meaning clear?

``So what you were saying is…….''

Then, Duke Fan Yue confessed with an indignant expression.

"The Heavenly Blossom Sword is traitor who dare to defame the Heavenly Emperor with their absurd and absurd claims. Therefore, please issue the order. I will deal with her discreetly and erase her from the world."