\chapter{Lineage (13)}

'Yeonsul, raise your head.'

How could she not understand the gravity of what it means if the Emperor adressed her that way?

\textit{Did the Empress finally cracked and spilled the beans?}

\textit{Well with the Crown Prince wedding and all that dreadful news going around how could Empress Mama just sit back and watch her children get hitched?}

\textit{Maybe a hint would’ve been nice…}

``Guh—''

``Get that veil off your face.''

Qing obediently pulled down her face covering.

The Emperor quietly scrutinized Qing’s face.

It was the first time he was seeing her unmasked since she had entered the palace.

During the previous audience he hadn’t bothered to ask for her veil to be removed because he planned to shove her away to some remote corner of the Forbidden City and never look back.

That sheepish expression of hers quickly glancing sideways to gauge the mood was familiar.

At this rate it was no surprise the Empress could recognize her at a glance.

``A princess from the Central Plain was roaming outside the palace and it’s only when I called for you that you finally showed up? How audacious! Do you have any excuse?''

\textit{Well this doesn’t feel too welcoming…}

\textit{I mean if the Emperor was really her father one would expect him to ditch the serious royal demeanor and say ``Come here let me hug you just once'' right? So surely the Empress would’ve let it all slip about who I really am by now.}

\textit{I heard that even the younger giant Yuansui had a strict and harsh father that made her timid whenever she stood before him.}

Qing was soaked in affection.

But without that affection she wouldn’t reciprocate.

Sure she shrank back in front of him but now that the Emperor was acting this way it made it easier for her to speak up.

``Your Majesty, I am not the Yuansui of Forbidden City; I am Ximen Qing of Divine Maiden Sect. I have no memory of my past so I can’t claim to be a princess and I fear having the gall to endure your slander.''

\textit{That was something I should have told the Empress ages ago.}

\textit{But how could I have said that in front of her?}

\textit{It’s easier to say in front of the unloving Emperor.}

``You are not Yuansui?''

``Exactly I too don’t know the truth so I can’t give you a definite answer—''

``You are Yuansui.''

\textit{Well if it’s the Emperor that’s the end of that. He cuts me off.}

\textit{And if he’s claiming I’m a princess well that’s just the logic he’s rolling with—}

``You must have witnessed the Celestial Maiden Temple’s great ritual clearly. That was a rite that channels the power of the Divine Blood. You’ve witnessed its effects with your blood so the blood of the Emperor flows through you.''

\textit{Oh, is that so?}

\textit{When they drew blood from me it was all a bit suspicious while playing it off as a health check but it was practically a genetic test.}

\textit{That hammering the feats of strength—essentially a magical method of confirming paternity by blending the royal blood with a person’s blood.}

\textit{I’d had a strong suspicion there but now it looked like complete evidence was coming to light.}

Of course since she was practically certain already she wasn’t too shocked.

After all her struggles were more in mental spiritual terms—what’s strange in a world where people can wield laser swords use magic and waltz around with Jiangshi?

But still.

``I must respectfully disagree; I would rather live as a common Wulin individual.''

At that the Emperor scoffed.

``You’re amusing. You’ve been playing along with your mother pretending to get punished, yet you dare call yourself an ordinary person before the Empress and a Wulin individual before me?''

``Well the Empress is in a fragile state—''

``Enough. Had you been a mere commoner you would have faced the death penalty for mocking the Emperor yet as a part of the royal bloodline your family matter can be overlooked.''

\textit{Wait, is he subtly threatening me?}

\textit{Choose the Cheonhwa-geom and die; choose Yuansui and I get to be the rebellious daughter?}

``So now you must fulfill your duty. I have long intended to cleanse the world of these rebels in Wuilin so you too can join the Heaven in that purpose.''

``Your Majesty—''

"They have long been unworthy of the Heavenly Court's grace. I will spare the Shinnyeomun Gate. And there is no need for you to take up arms yourself. Princess Yuansui, having learned the horrific truth of Wulin, will personally report these traitors."

Ximen Qing was actually Princess Yuansui, and she had infiltrated Jianghu to personally investigate Wulin and determine whether its people were traitors or not.

And since they are a traitors, the Imperial Court would punish them.

Princess Yuansui was summoned to report this matter.

``Your Majesty—''

``Enough!''

``Wait, just hear me out for a moment!''

Qing dared to raise her voice.

I don't know why he hates the martial arts world so much, but perhaps it's a blind hatred bordering on madness, as Ziyou said.

But judging from the previous ritual and the fact that the strengthening of the Embroidered Guards was caried using the blood of criminals, he doesn't seem that crazy.

``Wulin individuals are not rebels! They uphold righteousness and chivalry better than anyone else; they contribute to the world!''

``Righteousness and chivalry? How charming. You combine those characters and call them righteous heroes; do you honestly not know what that means?''

Righteousness (義) was good and chivalry (俠) was good, but tie them together and ‘righteous heroes’ (義俠) was certainly not a term anyone would love to be called in the Central Plain.

In Qing’s homeland terms, it simply meant rascals thugs and gangsters.

``No! Even now, Wulin has righteous heroes, um, I mean chivalrous heroes, wait-''

‘Chivalrous heroes’ (Xiake\footnote{俠客}) sounds great but not something to utter before officials especially before the Emperor.

That word came from the legendary assassin Jing Ke who once intended to kill the First Emperor.

``Sure there are wicked folks but at least the orthodox martial world individuals strive for peace throughout the realm so please reconsider those words—''

"Hmph…"

The Emperor interrupted with a snort that was anything but kind.

Now that I think about it even the Empress never quite listened to others. The term ``balance'' might apply here.

``By your own words there are good people among martial world individuals but there are also vile villains who deserve nothing less than the worst punishments.''

``Ah.''

Qing’s expression brightened a bit.

\textit{Could it be?}

\textit{Is this a situation where we might resolve things through conversation?}

But that hope was short-lived.

``However whether it’s a good hero or a vile rogue all Wulin individuals are harmful to the world. Their very existence iss a pestilent threat to peace so you can imagine how I found that laughable.''

The Emperor’s expression was so calm as if he were stating a matter of fact.

\textit{Had he shown the slightest hint of hatred I could’ve dismissed him as simply mad.}

\textit{But why though?}

``Long ago when Grandmaster Wutian dared to invade the Forbidden City and commit great crimes, he even laid hands on the Emperor’s sacred body to intimidate him. He dragged him by the collar up to the highest point of Huanggu Hall and shamelessly demanded proper governance.''

Qing had heard of this story before.

The royal family’s misdeeds were so rampant that back in the day Celestial Martial Emperor invaded the Forbidden City, captured the Emperor and threatened him by saying 'Get it together or else' right?

``Do you know what the ancestor said to Wutian back then?''

``This girl will listen closely.''

``The ancestor smiled and said he would hand over the throne to Wutian. 'The strongest under heaven shall be the Emperor; if that’s the case wouldn’t peace reign as you say? So sit upon the Emperor's steps and govern the realm', he said.''

This was new information for Qing.

She had imagined the Emperor would’ve begged for mercy in a cowardly fashion.

By the Emperor’s account rather than being in utter chaos the Grandmaster who stormed into the royal palace also wasn’t some mere nobody.

Being caught and bickering while hanging in the air smiling and saying `Then you be the Emperor' was quite something.

``And Wutian replied ‘Not a chance. How could I possibly do such a troublesome task? I’m barely managing my own affairs. Stop talking nonsense and do the right thing.’''

``Ah.''

Well that made sense.

He was just an old man who was all about training and showing off for his juniors every now and then.

Qing could vouch for that since she confirmed the personality of the old man while circling Absolute Sword Walls.

This made her completely assured.

``From that moment the Heavenly Mandate and Wulin could no longer coexist. Do you understand?''

\textit{So it’s essentially a vendetta from the ancestors?}

\textit{Merely personal um family-related? Nonetheless a private reason to torch Wulin?}

\textit{How am I supposed to reconcile with that?}

\textit{Does he think I as Yuansui share that ancestor’s grudge too?}

``You really don’t get it do you?''

``Huh?''

``Your expression tells me you’re puzzled. And since you don’t understand you’ve no intention of conforming even a smidgen.''

``But that’s not an excuse—''

``You’ve always been this way. You trembled before your father, constantly being wary, yet you still never correct your behavior. That’s because in your mind it isn’t wrong. To you it’s simply an unjust scolding. Even when memories lost the spirit remains.''

Yuansui enjoyed mingling with her servants without any pretense.

Sure there was a limit to being friendly but treating them like family was a stretch.

Despite the Emperor’s multiple scoldings he would still say that a dignified figure should never show weakness to those beneath him and the princess must be distant from the needy.

However before him Yuansui always replied with a 'Yes I understand' while never changing.

That’s because to her fondness for those who love her regardless of status was what’s right.

All of her actions followed suit.

Whether it was her mother the nurse or even the defiant eight-year-olds she would still carry on as she pleased.

Her affection was out of respect for those who cherished her—somehow everyone was a good thing to her.

She sneaked out to catch a glimpse of the world outside the palace.

Through persistent pleading she finally went out into the open.

The very existence of the Divine Blood beyond the palace posed a significant risk to her people and who knew what might happen if something went awry?

What could possibly happen with a simple outing? After all it’s not like Beijing with its sacred fortress could be too dangerous right?

She even begged for protection to learn swordsmanship.

She couldn’t comprehend why learning swordplay would be prohibited especially for royal princes—it was just for fun!

She wouldn’t budge on what she considered right nor would she act on what she thought was wrong.

``Of course you probably didn’t have such a steadfast belief. But that was your nature. If you didn’t accept it yourself others’ advice felt like mere meddling or nagging.''

The Emperor clearly knew that she practiced martial arts.

After all it’s not like anything could escape the Forbidden City eyes and ears.

\textit{Honestly just hearing about how much trouble Yuansui was back in the day—she really was quite the troublesome child!}

``You need to grasp the harm Wulin poses. Understand why it must be eradicated and how it threatens the world with its very essence.''

``This girl will listen closely.''

So the Emperor took a moment seemingly picking his words carefully tapping the elaborate armrest of his royal seat repeatedly.

Then a while later he finally spoke.

``Grandmaster Wutian should have respected the Emperor’s might. Otherwise he should have never laid a finger on the Emperor’s body.''

``…May I ask why?''

``Do you know what kind of being a true Emperor is? Do you understand the duty bestowed upon us from Heaven and what kind of governance the Emperor should practice?''

\textit{Huh? Was he trying to lecture me while asking me questions?}

As Qing stammered she caught a glimpse of disdain in the Emperor’s gaze.

It was a moment filled with bitterness.

The Emperor began to speak to himself with a solemn voice as if he were responding to his own inquiries.

``The Emperor exists above the people.''