\chapter{Lineage (12)}

After that, the hammering continued for a while.

Back in Sichuan during the peak of Qing’s supremacy the master was writhing from the heavy strike of an enormous club-like sword out of transcendental mastery like a chaotic giant swinging around.

Despite the prolonged hammering rather than grimacing a blissful smile crept onto his face that he could hardly contain.

The Emperor lounging with his heels resting on the armrest rested his chin in his hand casting a disinterested gaze at the scene.

Inside however he was quite the jumble of thoughts.

He was invoking the Heavenly Gift Technique a profound method that harnessed nature’s grace.

This wasn’t a fancy name bestowed by the palace like the Imperial Martial Arts; it was the original name written in the Central Plain language from the ancient scriptures.

With that magical technique from Tianzhu it was something that solidified a person’s body through the rare blood of precious nobility.

Those reckless Tianzhu barbarians dared to differentiate the highborn from the lowly amongst their kind as if they were above the heavens.

Thus this technique was a grace from the higher class of Tianzhu bestowed upon those they deemed lowly.

However for the people of the Central Plain there were no social classes.

Except for the Emperor everyone was simply equal human beings; worth was only attributed to high or low official positions.

After all the Emperor wasn’t just any man.

The Emperor was a divine being the son of the heavens.

Thus the power of the Heavenly Gift Technique which used the blood of the Emperor was so overwhelming that even Asiya who had conducted the ritual was left flabbergasted unable to hide her confusion.

In the original method a precious cup of blood was typically required and the vessels of Tianzhu were much larger than those of the Central Plain.

However it wasn’t feasible to extract that much blood from the Emperor.

So even though a minuscule amount less than half of the usual required quantity was used the outcome was more than double what anyone could have predicted causing quite a stir.

If Master Danlun had been present he would have explained that it was only natural.

The highest class in Tianzhu were the priests.

The word priest denotes one who manages the affairs of the gods; so priests were administrators tending to divine duties.

Though they were close to being divine they were still not gods meaning even if the Tianzhu people regarded them as noble blood they couldn’t escape their humanity.

However the Emperor was divine.

He was a direct descendant of those ancient celestial beings who out of affection looked after mankind and the Emperor bore their bloodline.

One could question how the current Zhu clan retained such blood yet isn’t the power of the technique derived from belief and emotion rather than mere facts and logic?

The Emperor tapped his fingers on the armrest.

A habitual action whenever lost in thought.

The ritual was successful.

Five new loyal subjects of the Heavenly Gift were born; they would become zealous followers serving the Emperor as witnesses to miracles.

Nonetheless it wasn’t guaranteed that everyone would succeed in this grand undertaking.

At least one among them was supposed to have failed smeared against the hammer pouring out blood and perishing in the validation process.

It wasn’t uncommon for the grand ritual to witness at least one failure.

This calamity befell those who feigned loyalty but harbored disloyalty for those high-ranking palace officials privy to the secrecy made sure to empty their own offspring or followers out of greed.

Thus while those imbued with the Emperor’s precious blood would survive those receiving other blood types would die if their effect didn’t manifest as they were smashed by the hammer.

Among this group of grand ritual participants there was one picked by the Warrior who had received the blood of someone other than the Emperor namely Ximen Qing.

Normally that would mean death by the hammer and a failed candidate thrown in had indeed been expected to perish.

``How did that one fare? Was the ritual indeed assured?''

A voice echoed in a solitary room.

From behind the Emperor a shadow slipped forth quietly signaling a secretive warrior.

``Not merely assured, it was exceptionally solid—twice as tough as the others making even I had quite the challenge disposing of the remains.''

Occasionally the successful warriors of the grand ritual would be found exploded overnight discovered as mere scattered flesh chunks.

These would be those with bad rep who were disrespectful to higher-ups or those who abused their subordinates or even the greedy types who sold off royal insignias too recklessly (though selling itself was legal).

This served as a warning that even those who received the grace of heaven for being loyal were struck down if they acted greedily against the realm.

Thus the Heavenly Gift practitioner had been able to shrewdly prevent such evil deeds.

Of course it came with side effects.

In turn the Heavenly Gift practitioners became ever haughtier as their mere survival began to feel like heaven’s license filling them with excessive confidence.

``Twice as tough huh?''

``Recently she consumed multiple elixirs so perhaps the residual effects were strong enough to influence the blood. That’s my thought on it.''

If Master Danlun were aware of all of Qing’s circumstances he might have interpreted it differently.

Qing was the current leader of the Divine Sect and not just of the Zhu heavenly bloodline; she was in fact the essence of heaven itself a living bodhisattva an existing sage which likely influenced the technique.

However the Emperor was not as versed in magic as Master Danlun was nor was he knowledgeable about the current situation of the sorcery sect.

Thus the view of the experienced warrior reigned reasonable making the Emperor agree.

\textit{The conclusion was clear.}

\textit{Ximen Qing carried precious blood.}

\textit{The blood of Heavenly Zhu flowed within her.}

\textit{Ximen Qing… truly is Princess Yuansui.}

The Emperor slowly closed his eyes.

The Queen’s mania wasn’t madness after all.

At the time without knowing one might think the current princess seemed less than regal but as it turned out having died and returned only to lose her memory; she had been re-learning the palace laws she followed.

Tap tap.

For quite some time the only sound echoing in the quiet room was the Emperor’s finger drumming.

And finally

``Bring Ximen Qing, no Yuansui here.''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Grandmaster Beom-yak was the bodyguard at Huanggu Hall.

Ordinarily he couldn’t stray from the integrated three palaces of Huanggu Hall and the two behind it.

To be precise he was not allowed to pass through the northern realm of the palace where other masters resided the Emperor’s secret guards.

Of course how could other masters notice a master sneaking in unless they were of the same caliber?

Thus the Emperor’s secret guards acted as an invisible line preventing Grandmaster Beom-yak from crossing to the North realm of the Forbidden City.

However it wasn’t the case for Namsamso.

Namsamso was located to the east of Huanggu Hall meaning he could stay there all year without ever encountering the bodyguard.

Therefore there it was – Namsamso the Healing Room.

There was no direct evidence that Cheonhwa-geom was daring enough to impersonate the blood of the Tianzhu princess.

Basically denying it outright while ambiguously maintaining a defensive stance.

If a most easily obtainable evidence like a witness were sought it would be Lady Deokseong or Haeryu.

But those two already recognized Cheonhwa-geom as the true princess and they wouldn’t be one to throw their lives away for such a trivial matter.

So where on earth could one find evidence?

In fact there was no need to find it!

Because one could just fabricate it!

``Do you perhaps wish to leave the palace? There’s a major traitor within and if you contribute to subduing such an adversary you could very well leave with expansive lands!''

``Really?!''

The palace maids who tended to the Healing Room swallowed nervously.

If one were to list the dreams of these maids undoubtedly ascending to the Emperor’s harem would be at the top.

But the likelihood of that was extremely slim.

Those noble ladies were undoubtedly of some divinely beautiful countenance while the jaded nobles might only chase after a commoner’s face.

The second option varied depending on the individual.

To become a favored maid of the Queen or Chief Consort and then rule the Forbidden City as a powerful maid.

Otherwise be recognized for great deeds and leave with a pile of land deeds.

Grandmaster Beom-yak was suggesting the latter: leaving the palace with the title of ‘madam’ and living in luxury for the rest of her days.

``B-but my lady how could a young girl like me…''

``Fret not. I wouldn’t ask you to do difficult tasks; it’s merely to testify so your safety was in no jeopardy.''

``To testify you say?''

The maid swallowed hard.

In truth how many schemes like this have been circulating in the palace already so she understood the insinuation immediately.

In the Forbidden City where personal sorcery was a taboo the accusation and testimonies of maids served as a powerful weapon.

Grandmaster Beom-yak then smiled kindly.

``Moreover this comes from the Crown Prince’s wishes. Even if you wish not to leave the palace serving His Highness might present a magnificent opportunity.''

``Gasp.''

The maid held her breath.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Hearing the Emperor called for her Qing felt her heartbeat quicken.

No matter how much she was Qing it was only natural to feel tense at the Emperor’s call.

After all it was a summons from the highest authority in the Central Plain entrusted with life and death over countless individuals.

Furthermore quite a figure the Emperor was.

Just considering past events his brilliance was truly striking.

In Sichuan he was the callous brother that attempted to kill his own sibling.

On the road to Gwangju he displayed an alarming rage disorder when confronted with a brother unwilling to die resulting in numerous casualties.

And facing the students of Yijeong Muhak Institute he behaved like a tyrant who saw the people as mere pawns.

Not to mention the recent bloodbath of Tianyeosa and the trial of strength which certainly wasn’t viewed positively.

Sure the insidious ritual was one thing—using humans and beasts as materials was indeed outstanding.

Nonetheless among those rewarded was not a participant of the ritual but rather numerous animals that should have been sacrificial materials—over a hundred in fact.

Though despite that the Emperor’s influence seemed stuck on a mere zero.

Anyway.

There was no doubt that he was a person who would thoroughly erase anyone in his way without a second thought.

Could such a man not control his anger?

If something irked him he’d likely erupt into a furious demand to ``beat that woman until her bones shatter'' and might even toss in ``burn Divine Maiden Sect and Martial Alliance'' as he extended his blade—of course one could bet on it safely.

However if things got dicey she was confident she could slip away unharmed.

But then how would she deal with the aftermath?

Thus Qing maintained an excruciating caution akin to a beauty from the Ximen lineage.

And so she approached the main palace of the Forbidden City the Inner Palace.

Among them the Emperor’s quarters the Geoncheong Palace.

The Inner Palace’s sections were sacred ground for men.

Only a royal prince could venture here with the Emperor’s consent.

By law even the Crown Prince should not set foot into the very heart of the Forbidden City.

So those who could step into the hallowed Grounds of the Inner Palace were women of the palace and eunuchs only.

Of course in the primitive Central Plain of antiquity gender recognition was nonexistent and suggesting such would earn one a swift beating labeled as possessed by spirits.

Thus in Central Plain customs Qing was accepted as a woman.

Which meant she could enter the Inner Palace.

And so within the Geoncheong Palace!

Crossing through the doors opened by eunuchs from both sides she meandered through the maze-like corridors cloaked in screens finally reaching the threshold of the Emperor’s private chambers.

This room within Geoncheong Palace could be filled with monumental writings unparalleled in history itself.

Of course Qing had no way of knowing that.

Nor did she have the bandwidth to ponder such matters.

She was merely overly cautious so that she wouldn’t give anyone a chance to find fault.

Thus as she nearly clung to the ground ready to shout out ``Long Live the Emperor!''

``Hmm.''

``It’s enough.''

The Emperor signaled her to cease her enthusiastic call for victory.

Ah that was unexpected.

``Enough'' could mean she didn’t need to perform the entire three cheers or perhaps even that she could skip the whole salute altogether.

Just as Qing was paused in thought the Emperor’s voice echoed in the air.

``Now that it’s sufficient, Yuansui, raise your head.''