\chapter{Lineage (9)}

The Empress was just happy every day these days.

Because she was a child she had once lost, she missed her even more, and every moment was precious and she feel regretful and sad as it passes.

Lately, there's been a strange phenomenon where the palace maids doing chores trembled just by making eye contact.

Wouldn't it be normal for the inferior to fear the superior?

Even now, she was enjoying the luxury of being massaged by her daughter's fern-like hands (which were quite large for a fern, but a child was always small to a mother) -

But, what about the level of massage?

Did she learned massage instead of martial arts? Why was that?

Anyway, except for the fact that it was very cool when touching, her hands were as skilled as those of a skilled court lady. In fact, it was good because it was a hot day.

A mother who receives a massage from her child will probably say that it was all good.

``Good, really good.''

The Empress's eyes turned red as she felt the comfort of her child's hand rubbing her shoulder, saying that she was now all grown up.

At the same time, a certain resolution takes hold.

\textit{I must send the child back into the world, into the cruel world of Jianghu, swept by the fierce storms.}

\textit{It may be safe to hold a child in my arms and wrap it in the hem of my skirt, but is that really what the child wants?}

She was a big kid who had been running around the Forbidden City area since she was little.

She was a young princess who was so curious about what was going on outside the palace that she would nag the palace attendants and eventually end up telling them everything. So, how much do the palace attendants actually know about the world outside the Forbidden City?

In the Qing hometown way of thinking, it was no different from the trainees at the boot camp asking their instructors about the life of a regular unit.

Those assistants must have heard it only as a passing rumor from an unknown source, so of course they don't know anything.

Anyway, she was a princess who has been curious about the outside world since she was little.

That child, now all grown up, comforted his mother's shoulder and told her the story of her experiences, of traveling around the world under the vast sky.

"Oh, and I also went to Qinghai. There was this weird guy there, oh, his nickname is Strange Monk, really. He was a really weird guy. The walls there were painted white. It wasn't even a hot place, was it? Oh, that's right, in hot regions, they paint the walls white to keep things cool…"

It's a story without context or order, but the amount of activities was still amazing.

Beyond the vast desert, from the southernmost Guangxi land to the easternmost Shandong Peninsula, and to the westernmost Qinghai land.

\textit{Having traveled all over Zhongyuan in just a few years, even if she had lost her memories, wouldn't the stifling life in the palace have been deeply etched in her heart?}

\textit{How could it be so-}

``Oh, right. And I have a daughter.''

``Yes, yes, you have a daughter, huh? What, what happened?''

The Empress jumped up from her seated position.

\textit{What were you talking about! A daughter all of a sudden!}

"Her name iss Ciyu. She's kind and gentle. Her gaze are a bit rotten, but that's cute in its own way. But when she smiles, she's as bright as any normal kid, so I feel a little reassured."

``No, what the heck is this?''

"Her gaze? I guess it can't be helped, given her young age—"

``No, no, before that, daughter? The father, who is her father?''

``Oh, that. Just a moment. So, let’s see, Dad. So, Dad, Dad, um, here, Changming, Murong, Chunfeng…''

Qing counted each fingers one by one.

\textit{My daughter, whom I haven't seen in a long time, said she had a daughter.}

\textit{When I asked her who the father was, she muttered names I didn't know and counted by opening and closing her fingers.}

\textit{As if she doesn't know who the father is.}

The Empress's mind was so dizzy that all the strength in her body suddenly drained away.

\textit{No, no matter how, no matter how different the world was outside, no, oh, my precious daughter, oh my… … .}

``Ah, I got confused. They're not the Dad, ther're Moms. I’m the Dad. Eh, Your Majesty? Are you okay?''

``Y-y-you bitch! Yes, you bitch! Lady Cho, fetch a whip, fetch a whip right now……!''

``…….''

There was no answer.

It seems that Lady Cho has already fainted.

In fact, the Empress's current state of health was thanks to the precious tonics that Qing had offered her.

In Qing's homeland, the saying, 'giving a sick person medicine' refers to this situation, and in Zhongyuan style, it was expressed as 'slapping someone on the cheek once and then hugging them three times.'

Anyway.

The misunderstanding was quickly resolved.

``So, you mean she’s an adopted daughter?''

"Yes."

"You little brat, you haven't even gotten married yet. No, what kind of child can you have before that? What kind of nonsense is this?"

"Hehe, I knew I was lacking, but she was similar to me, and I wanted to take responsibility for her. There was no one else who can."

Before Qing took her om, Ciyu was nothing more than an evil tool used in the Blood Cult's tactics.

Even if Shaolin Temple was just a pseudo-Buddhist sect that focused on martial arts, wouldn't it have been to the extent that even Great Monk Wunue, who learned the teachings of Buddhism, was insisting she should be locked up in the Repentance Hall for eternity?

But it was not at the level of such an obligation.

\textit{At first, the expressionless little girl would awkwardly looked around and try hard not to move, but now she often smiled and hugged me without hesitation.}

\textit{Now, when she grow up, she might hit puberty and become a delinquent, but surely, our Ciyu, won't be like that. Right… right?}

Looking at the restless Qing, the Empress felt sorry.

How cruel it must be for a mother to introduce her child and make her child look so stern.

As much as I cherished my child, wouldn't I cherish my daughter as well?

"Ahem. I wish I could at least see her face. I can't even see my granddaughter's face. I guess I'll have to find auspiciuous time to perform ancestral rites at the Divine Maiden Sect."

The empress was still not pleased with that child named Ciyu.

However, the love of an old person for his or her grandchildren was like an instinct ingrained in his or her genes, so it was impossible to guarantee that he or she will still feel dissatisfied with it even after seeing it in person…

… … was bullshit.

She was already a mother with a child at a time when she was still in the prime of her life. So how will her future marriage be?

Even her mother said her eyes were dirty, so she must have really dirty eyes.

Surely that little thing must be the kind of girl who opens her eyes wide and stares at me like that, and if that little thing was already acting like that, well, if it's acting like that, it must be cute like a horned calf… … .

No, no. How could this reckless brat suddenly take a child in and call her his granddaughter? And call me his grandmother? Grandma.

Um. Grandma. And granddaughter. My granddaughter.

After Qing left, the Empress's heart was already pounding as she lay in bed.

Yes, that girl, Yuansui, is a filial daughter.

\textit{It's incredibly strange for a woman to call herself a father, but what's the big deal? She's my granddaughter.}

\textit{A granddaughter? That's something I never imagined.}

The prince has no interest in women, and the Emperor had no intention of taking a concubine, so it was far from time to time that he will see the crown prince.

When a princess gets married, she truly goes far away forever. She was someone who leaves for a faraway land, a barbarian land, with no hope of seeing her again in the rest of her life.

\textit{So, my granddaughter?}

\textit{This is so annoying. How could she not have said a word to her mother all this time? If she had given me a letter earlier, I could have gone to the ancestral rites and seen her face, even if it meant going to great lengths.}

The empress was already gripped by the urge to see her granddaughter's face and couldn't sleep at all.

So the next day, I woke up in the morning with a very tired look on my face and slowly went to work at the Gonyeong Palace.

This was the Empress's job to look after the internal affairs of the imperial family, as the Empress was the head of the eunuch organization called the Twenty-Four Secretariats of the palace, the organization that operates the Forbidden City, and the mistress of the imperial family.

however?

What was the status of the submitted report?

'In the royal palace, newly made folding screens, furniture, ivory, apples, and sandalwood were presented.'

'Didn't the private sector come up with a plan to make a new curtain to hang over the bedroom?'

'The Sangseongam has already prepared a grand banquet and requested an edict to gather special products from each region.'

'The Insugam requested permission to visit the Naejanggo to create a jade tablet to award the new noble title.'

'The royal court must have sent a booklet discussing various patterns of silk to be used in new attire.'

All these tasks converged in one direction.

If we interpret it in the eunuchs' speech according to historical facts, the meaning would be roughly like this.

'I'll make furniture for the new room.'

'We're making a bed for newlyweds. We want it to be soundproof and invisible.'

'I will thoroughly prepare the wedding food.'

'I'm planning to make an identity badge for the new royal family. Can I use your warehouse?'

'Please check if the fabric of the wedding dress is pretty.'

"What the heck, what the heck. Look, what the heck is all this? Is there some grand imperial event I don't know about? Doesn't it look like they're going to kill a thousand souls?"

The highest ranking eunuch, the eunuch of the royal family, was surprised and asked back.

"Yes? Your Majesty, it's for Crown Prince's wedding preparations. We'll choose an auspicious date, but we'll have to hurry as much as possible. Since time is of the essence, I've been given the order to prepare with great care."

"No way! Even if you're the Emperor, you can't decide on a state wedding on your own! How can you act so recklessly when all the courtiers were expressing their concerns…!"

"Your Majesty, the ministers of the six ministries have already declared their intention to uphold the will of Heaven. The seating arrangements of all the officials have already become a mess…"

The eunuchs were most concerned with arranging the seating arrangements for the event, as the good seats were limited and everyone wanted to get a good seat.

In other words, doesn't this mean that the subjects have already agreed and that a fierce battle for power was already unfolding behind the scenes?

``What the heck! Your Majesty, Your Majesty!!''

So, the Empress was angry.

The Angry Empress! Sortie!

"Your Majesty! What on earth is going on? How could you do this, how could you do this, without even asking the mother's opinion?"

The emperor sipped his fruit tea indifferently.

``It’s a hot day, but this is refreshing. Would you like a drink, Empress?''

However, his voice was slightly trembling, and the hand holding the teacup was shaking slightly. Although he was trying hard to appear calm, he seemed ready to run away.

That would be the case, for the Empress was the daughter of an outstanding military family that had held high-ranking positions in the Ministry of War for generations and produced countless famous generals.

That's why she had a fierce temperament and sharp hands.

``How can you say you’re being careless now! How can you give the Crown Prince to a woman like that, no, that, bitch, yes, that bitch! Uh, I don’t know where she came from, a dirtier, dirtier, dirtier bitch!''

The Empress took great pains to use harsh words that would not come out.

However, to the Emperor, it seemed as if she was trembling with anger, and caused the ripples of the fruit tea to become a little more violent.

"Ahem, Your Majesty. The ministers of the six ministries and all the officials have already promoted this wedding. Even if I am the Emperor, how can I ignore the loyalty of my subjects? Don't you understand?"

The emperor was proud.

Even if he was the emperor, he cannot push forward the country's events with his own will.

As the Empress thought, the Emperor's attempt to push for the wedding on his own was ultimately a futile attempt that did not need to be worried about.

And now it was the opposite.

All the ministers agree and step forward?

No matter how much the Empress objected, she could not cancel a national event on her own.

And didn't the Empress know this?

The Empress's eyes went dark!

\textit{How did things end up like this?}

Suddenly, her stomach tightened and her head started spinning, making her feel very dizzy.

It was as if she could hear the sound of blood drained from her body as if the veins were constricting.

In such a situation, the heart was pounding, anger was rising, but no sound comes out as if the throat was sewn shut.

The Empress managed to speak with great difficulty, her voice choked up.

"Why, why are you doing this? Yes? Your Majesty, please, it's my, my wish. Haven't I always supported your will? So, just this once, just this once, could you not step down? Your Majesty."

"Tch, I'm the one who should be complaining! Didn't I explain it clearly in good words? I even promised to keep the Crown Prince away from seeing her! And yet, how can you keep opposing me like this? What should I do next? Tch."

The emperor was shouting and gulping down the cold fruit tea as if his throat was parched.

``Ximen Qing is your daughter! Ximen Qing is Yuansui, our daughter Shaoxia!''

The emperor's eyes widen at that.

As the emperor stopped in his tracks, the fruit tea in his mouth flowed down like a waterfall.
