\chapter{Journey to Diancang (5)}

After breakfast, as the descent was approaching, Peng Cholye threw a casual flirtatious glance at Qing.

``Qing, were you heading back to the Shinnyemun? If you don't have any particular plans, why don't we go to Nanjing and relax for a bit? The weather was just perfect right now.''

Of course, if there was Beijing, there must also be Nanjing.

Nanjing, just below Beijing in the northern part of Hebei, could be considered a special city of sorts in Qing's hometown.

``I'm planning to visit the Diancang Sect,'' Qing replied.

``Diancang? In Yunnan? That far away?'' Peng Cholye raised an eyebrow.

``How about coming along if you have nothing to do?'' Qing asked.

Normally, Qing wouldn't have suggested joining, but things were different now.

Qing had Ciyu to look after.

It's better to have as many people around as possible, right?

Because Ciyu was a peculiar, celestial-like child.

What if, like last time, she gets caught dissecting animals while I'm away? If I'm there, it's not a problem, but what if I'm not around?

I mean, it's not that weird for a child to be curious and dissect animals. You could just say, ``Ah, she wants to be a doctor.'' What's the big deal?

Anyway, whatever.

Peng Cholye shook her head.

``At my age, going that far is a bit much, isn't it? But if you're leaving on a long journey, you'll need to pack up properly. I'll send a porter with you, so you can have him work for you, like a cow or a horse.''

``Really? You don't have to do that, Cholye.''

``No, it'll make me feel better. Go ahead, make use of him. Here, a strong porter for you. Use him as much as you want, haha.''

With a sinister laugh, Peng Cholye tapped her younger brother, Peng Daesan, on the shoulder, hard.

``What's that supposed to mean? Why would a man be following a woman's journey?''

``Is he always like this? I never heard any good rumors about him,'' said Tang Lan-Ah, raising her voice angrily.

As Peng Daesan just huffed and didn't say anything, Peng Cholye tilted her head in confusion.

``Are you sure you don't want to go with me? Yunnan's a bit far, but we could stop by Sichuan first.''

``Sichuan, were you serious? Do you know how difficult the roads are? We have to go through Guizhou to get there,'' Tang Lan-Ah complained.

It seemed like she didn't want to go home either.

Despite the rough roads, how difficult could they be for Qing?

Still, the reason she didn't want to go back seemed like a boss who keeps lingering around after work just because the party was fun, even if they're tired.

Qing turned her head toward the conversation.

Murong Zhuji, catching her gaze, lowered her long eyelashes.

``Well, I've promised to oversee Jun's training, and I also have to observe my mother's memorial…''

``Ah, then I understand.''

``But, but, if you really need me…'' she stammered.

``Ah, no need to worry. Family first. As for me, it doesn't matter if I collapse on the street, right?'' Qing's eyes narrowed.

``Oh! I didn't mean it that way…''

``Ha, I'm just joking,'' Qing said with a smile, trying to ease the awkwardness.

Murong Zhuji still had a reluctant expression on her face, but family always came first.

``So, you're teaching the Sword Sect, huh?'' Qing asked.

``Yes, I have been moved deeply by the dedication of these disciples. Their passion for swordsmanship was truly inspiring! How could I miss the chance to assist them? I'm already excited to discuss swordsmanship with them.''

The disciples of the swordsmanship academy would most likely join the Wulin Alliance's combat division as the Seogeomdan (Sword Division). After all, they had enrolled with the agreement to serve the academy for three years after their training. Whether or not they had signed that contract, how could they refuse an opportunity to join the Wulin Alliance's official combat units?

It was more of a privilege, akin to a special appointment by a large corporation, rather than an indentured contract.

``How about Chunfeng? Not going?''

``Me? You mean this Sima-lang?'' Chunfeng asked, confused, as he muttered about the name.

``Well, if you have time, you can go to the Diancang Sect first, and if you like, you can check out the surrounding areas,'' Qing said.

``Hmm, Qing. As the youngest vice-general of the Wulin Alliance, you're at the center of everything, and the Wulin Alliance can't function without you. But I understand your desire to connect with the Qinghwa Sword Sect,'' Chunfeng said with a chuckle.

But Qing didn't expect such a response, yet it was true that all things in the martial world were connected to the Wulin Alliance.

``So, you want to go to Yunnan too?'' Qing said, raising her eyebrow.

``Yes! Do you know about the Shibamanta Mountain in Yunnan? It's one of the most famous scenic spots in the region, and they say you can't call your life complete unless you've seen it once!'' Zhuge Lixian said proudly.

Qing glanced between Zhuge Lixian and Sima-lang, both of whom had their own reasons for going. One was a busy member of the Wulin Alliance, and the other was off to enjoy himself.

Zhuge Lixian smiled widely at Qing's reaction.

``You see, the true wise man was someone who runs his own business. He doesn't have to bow to others. The intelligent one lets others do the work while he focuses on his own goals. Meanwhile, the ignorant ones work for others' profit,'' Zhuge Lixian said, almost as if lecturing Qing.

Qing's face tightened as the words reminded her of the kind of speech from a pyramid scheme. But before she could say anything, Zhuge Lixian smiled again.

``Though, we do have our own way of working. The Wulin Alliance has its rules, but we, as the Zhuge Clan, move for our own people.''

Qing raised an eyebrow. The Zhuge Clan was known for being cunning and ambitious in ways that rivaled the Wulin Alliance itself.

Sima-lang, noticing this, retorted sharply, ``Aren't you a little too proud to be a follower of that ideology? What did we learn from history? Those who gain power for themselves often end up being consumed by it.''

Qing turned to listen, sensing the tension between them.

``Well, in the end, every leader will follow his own path, and every faction will align with their own goals,'' she said, her tone light but reflective.

Zhuge Lixian smiled, and both of them fell into a quiet, thoughtful mood.

Judging by the reactions, it seems the battle has been decided.

Well, Zhuge Lixian couldn't refute it.

But if you think about it, was it not true that Gongmyeong was an eternal loyalist, while Jungdal was a betrayer of the Zhongyuan and a conniving villain who became one of the Four Kings of the Southern Hegemony?

Then, Sima Chunfeng, who works for the Wulin Alliance, would be a better person than Zhuge Lixian, who wishes to serve his family.

On the other hand, if you were to argue that, it would mean insulting his ancestors.

In short, it was a no-win situation.

Qing internally recalculated the IQ rankings of her acquaintances.

From this alone, it was obvious who was number one in intelligence—none other than the man who could move others with his deadly charm and brilliant intellect…

Congratulations to Seolga for winning the number one spot!

The second spot goes to Chunfeng, the brilliant mind.

The third spot belongs to Nanna, the doctor and poison master.

Zhuge Lixian, however, was an exception!

``What about Changbin? You don't have anything to do, right? Want to come?''

``Shouldn't I ask my master for permission first…?''

``Ah, right. I suppose that's something we can't avoid.''

People from prestigious families could wander about freely, but those from major factions couldn't travel as they pleased. If they wanted to take a trip far away, they had to get permission from their sect.

If it was just a short detour, it was fine, but traveling all the way to the edge of the Zhongyuan would definitely require approval from the sect.

Still, Changbin's face as he sighed with relief seemed somewhat displeasing.

Why does he look so relieved about something that should be a hassle?

Qing glanced at the other instructors sitting nearby and asked if they wanted to join.

It was more of a polite offer than a serious invitation, as it would have been rude not to ask them. But when she asked, they all answered without hesitation.

``Well, I'm afraid I'll have to pass. I have too many responsibilities in the sect,'' said Yook-Ah, with a perfectly indifferent expression.

``Same for me,'' said Wolbong, his face showing no sign of regret.

It seemed the travel companions for the journey to Diancang Sect had already been decided.

On the way, Jangmyung would take them to the Shinnyemun, and then they would stop by Seolgasanghoe to pick up some items for Qing.

A sly smile crossed Qing's face as she thought of the long-awaited adventure ahead.

``I've been starving for it. Finally, it's time!'' Qing muttered to herself.

Just as she was deep in thought, a hand subtly tugged at her sleeve.

``Qing, what about me?'' Seoliri asked, her expression a mix of uncertainty and eagerness.

``Huh? You're already coming with us, aren't you?'' Qing replied, slightly surprised.

Seoliri's expression shifted into something more subtle.

For a moment, Qing caught the glimmer in her eyes.

``Wait a second. Why was this little chick tagging along with such certainty?'' Tang Lan-Ah snarled, her voice sharp.

Seoliri clung to Qing's arm, a determined look on her face.

``I'm always with you,'' she said firmly.

``No, it's not fair. This little chick has been with you the whole time, right? Isn't that a little bit unfair?'' Tang Lan-Ah insisted, her voice rising.

In the Zhongyuan, calling someone a ``chicken'' was a derogatory term used to mean they were foolish—basically, a ``blockhead.''

Seoliri was being called a ``chicken'' in a similar way.

Though, it wasn't entirely untrue. Guyeong was indeed a bit foolish—there was no denying it.

The only person she could comfortably speak to like this was Tang Lan-Ah, with whom she often used sharp words to express their friendship.

``Yes, I've been with her. But that doesn't make it unfair, does it?'' Guyeong said, a hint of embarrassment in her voice.

Qing raised an eyebrow at the banter between the two.

``Alright, I guess it's fine. We've been through all this together,'' Qing said, stepping forward and grabbing both Ciyu and Jangmyung's hands.

It was time to head home.

Though, it didn't really feel like returning home. The master wasn't there, so it didn't feel like a ``homecoming'' in the traditional sense. It was more about stopping by to see the disciples, drop off a letter for the master, and then send one to the teacher as well.

The trip to Beijing had been uneventful, boring even. But somehow, the trip to Diancang felt like it would be lively, and Qing had a good feeling about it.

Whether her feeling was based on anything concrete or just a fleeting sense of hope, no one could say.

The distance to Diancang was roughly 5,500 li.