\chapter{Journey to Diancang (4)}

Now, with only a little bit of the academic schedule left, Qing found herself struggling with the aftereffects of her lazy wandering. Her legs ached, and after skipping out on rest time, she dove headfirst into after-school training.

However, when she saw Ciyu practicing awkwardly with a sword in the corner of the training hall, her eyebrows involuntarily furrowed.

Her father had come back after being away for so long but hadn't bothered to play with her—was she doing some kind of demonstration?

If it was a demonstration, that would be one thing, but it wasn't even a demonstration. It felt more like Ciyu was simply trying to get attention, like, ``Here I am, Daddy, look at me!''

The little one should speak up if she has a complaint; still sneaking glances like that? She's shrinking into herself, just trying to catch Qing's attention.

At least, on the bright side, Qing's father might be indifferent, but at least Ciyu has many mothers.

``Hey, daughter. You're already swinging a sword? What's this? It's a little too fierce. A lady should be elegant, graceful, and feminine, not… violent.''

``Mm…''

``So, do it gracefully. Throw the sword out with elegance.''

``…?''

When Tang Lan-Ah swung her arm, six sharp knives appeared between her fingers, three per hand, forming a total of six blades.

``Wow.''

Ciyu clapped her hands in awe, and Tang Lan-Ah's nose lifted in pride.

Tang Lan-Ah was surprisingly warm? Despite her usual coercive, villainous demeanor, she had an unexpected talent for dealing with children—could she be the sweet villainess after all?

Qing took another look at her, realizing Tang Lan-Ah wasn't as bad as she thought.

With that glance, Tang Lan-Ah wore a wicked smile, hidden from sight. If you want to catch a person, you start with the child, just like how you catch the general by capturing the expensive warhorse—catching the general was useless.

This was a devious act disguised as kindness, but Ciyu's eyes were sparkling nonetheless.

``Hey, birdbrain. Go stand over there. Training was about real practice. If you only aim at stationary targets, you won't improve. Make my daughter your target.''

``No.''

Gunyeong, who had always been around Ciyu, seemed to be feeling a sense of urgency. Every night, he would stealthily sneak out and stay near Ciyu, just existing nearby.

But that was all she did, she didn't interact.

Naturally, since Gunyeong lacked the social skills to approach, she just stayed close, silently.

At least this allowed Qing to focus on her training and teaching.

Thus, time passed at Yizheng Martial Study Academy.

The end of the academic schedule arrived!

It was time for the closing ceremony.

Some of the students had been top-tier warriors even before entering the academy, well-known figures in the Wulin. While some from the local martial factions were highly respected in their regions, many of them had been wandering, with no significant accomplishments.

Therefore, most of them were filled with pride, knowing that this time, they had finally achieved something meaningful in their lives.

With their proud faces, they stood tall and awaited the closing ceremony.

``The Academy Head will now give a speech.''

Immediately, their expressions darkened.

Suddenly, they remembered the major problem they had forgotten about all this time. Now they were filled with fear.

``When I saw the state of my trainees four months ago, they had fiery eyes full of thirst for learning. Looking at you now, I can hardly believe it. These great men, who have improved so much, I remember when I first left home, dreaming of joining the martial world. When I first entered the Wulin, I was just a naive beginner, encountering countless dangerous people and drawing my sword. Looking back now, I realize how much I've grown, but I remember a moment when I met the famous warrior, Five Iron Swords, and was defeated in just seventeen moves. I almost gave up and went back home, wanting to drown in a barrel of liquor. But then, I met Senior Yuseong, who asked me, ‘Are you eating well?' And I replied, ‘Yes.' I couldn't cry in front of him, so I resolved to eat well and move forward…''

This was the story of how he went from being a naive rookie to gaining the title of ‘Sword-dominating Dagger' after overcoming the swords of Five Iron Swords, eventually breaking the sword that once defeated him.

However, the one who didn't know that story was the one standing here—the respected elder of the Wulin, and the academy head.

``Now, as you all prepare to leave, I have three things to say. First…''

The trainees' faces turned pale.

'What is this? Why are these three things only being mentioned now?'

``First, distinguish between courage and recklessness. Stay alive and endure. The second most important thing was an unyielding spirit…''

Qing sighed with relief.

It was a good thing she had passed the speech duties onto Chunfeng, or she would've had to add something to this long speech herself. Just thinking about it was horrifying.

Time passed slowly, and the proud faces of the trainees began to shrink. Finally, they all looked exhausted, like people who hadn't slept, their faces darkening.

Only then could the closing ceremony continue.

The final part: the closing ceremony speech.

``Do you remember when you first entered this academy? Back then, you were just ordinary people, your names only known in your hometown, and you had no accomplishments. You were just commoners.''

But now, what has changed?

Sima Chunfeng smiled brightly.

``Of course, you're still commoners. But the world belongs to commoners, and geniuses merely lead from above. You needn't compare yourselves to them. How fortunate you are to see the stars shining in the sky, knowing the path ahead and being guided. I, Sima-lang, will be your North Star, guiding you to your destination—''

``Who let this bitch give a speech?!''

``Get her out of here! She's embarrassing the Military Department!''

``Everyone! What is a genius? It's someone who—wuh—wuh!''

During the speech, there was a minor commotion when warriors from the Wulin Alliance barged in and dragged out the speaker.

Afterward, the celebratory banquet continued.

``I thought the Instructor would be giving the speech,'' one of the students commented.

``Well, I've been away for a long time. And after coming back, I felt a bit embarrassed to speak in front of everyone,'' Qing replied.

At this, Yang Qi, a student who had competed with Qing during the entrance exam in Jocheong and had quickly reached a high level of mastery, smiled gently.

``I spent over three years learning swordsmanship at the Gohyeon Sword School in Jocheong. I received only a couple of teachings from the great swordmaster, Grandmaster Kang Yu. Honestly, most sword schools were like that,'' Yang Qi explained.

It's common that even if you join a prestigious sect to learn from a renowned master, you rarely meet the master, and it's often their disciples or even their disciples who teach.

``In comparison, Instructor, you've personally taught us. And thanks to you, we can proudly say that we learned the Sword of Qinghwa, a technique that you created,'' Yang Qi continued.

``Then it's just using my name, isn't it?'' Qing responded.

``But, Instructor, you are considered one of the top martial artists who will soon be known as the Greatest Under Heaven. If you achieve fame, we'll benefit from it too. So, we should be offering our deepest respects to you. Don't you agree!?''

``That's right!'' ``Absolutely!''

``Then, let me offer my gratitude,'' Yang Qi said politely, extending clasped hands in respect.

The noisy courtyard of the swordsmanship school suddenly fell silent, and all the students stood in unison, bowing toward Qing in a collective gesture of respect.

Qing opened her mouth awkwardly. She hadn't been around for long.

``Wait. Trainee Wan Talu, please get down. Don't climb onto the chairs. Oh, Trainee, don't do that,'' Qing interrupted, stopping one of the trainees who was about to stand on the table.

Not that she's a deceased poet or anything, but this gesture felt like something ordinary.\footnote{Dead Poet Society}

\textit{Is this a common cultural practice?}

After all, the official departure ceremony would be tomorrow morning.

The retreat today marked the end of his time here, and the departure would take an entire day of travel.

So today, he could drink and pass out without worry. It was a perfect opportunity to release the frustrations accumulated from the rigorous meals at the academy. The tables were filled with enormous amounts of liquor stacked in corners like mountains.

``A drink, Instructor?'' someone offered.

``Why was all this happening?'' Qing said as he poured a drink.

The swordsmanship students took turns pouring drinks, and if it weren't for Qing, one might think they were conspiring to get the instructor drunk. But Qing, as usual, never got drunk.

``Instructor, please take care of us from now on,'' one of the students said.

``Oh, you, the sword disciple. It's over for me now. You can call me freely. I heard you're taking charge of the troops.''

``I've already received your teachings, so you're still my instructor. Even though it was a short time, I've learned a lot. The disciples in the sword academy already know each other so well, and the training becomes less effective. To learn from a wider world and experience different sword techniques, I can't return just yet.''

``Oh, training,'' Qing nodded.

``Speaking of which, I heard that you're leading the upcoming generation of martial artists and gathering the chosen few of the Wulin world. Is there a chance I could join the gathering for the Sacred Sword of the Arcane?''

``Who said that?''

``Was it a secret?''

Qing was taken aback. The upcoming generation of martial artists leading a secretive gathering? Was it some secret society of stone masons?

Despite Qing's lack of intention, the public perception had already created this image, so the participants were really just members by name.

In any case, the goal achieved by the sword disciple, who was smiling brightly, also made Qing smile in appreciation.

``Wow, what a beauty,'' Qing thought as he admired the elegant sword disciple.

The scene was lively with everyone raising their glasses to Qing.

Once enemies like Soeumjo and Jangbihoo, who had poisoned and tried to kill each other in the past, now stood side by side as close friends. Before going to the palace, Soeumjo had been bitter about calling Jangbihoo an enemy, and Jangbihoo wasn't one to accept it either.

After two and a half months, they had become best friends.

Qing, continuously drinking, surveyed the room filled with noise.

This wasn't the end. Most of these people would be joining the Wulin Alliance's battle unit.

Next year, he would return to the academy for the next generation of disciples, and the hard training would begin again.

``Who the hell needs help!?''

``Fire's going to spread!'' ``Chang's disciple was at it again!''

Suddenly, a large spark soared from one corner of the room.

In front of it stood Chaeseongha, the Dance Master of the Blue Dragon, and two fierce-looking women at his side.

Changyo Hong, with an even fiercer demeanor, seemed to be looking for something to hit. As soon as their eyes met, Qing tilted his head.

It seemed like she had been searching for him.

Then, to Qing's surprise, Changyo Hong bowed her head, an unusual gesture for someone with such a fierce mouth.

The fire seemed to die down.

``Phew. Let's just exchange it, okay? If you don't like it, then forget it.''

``Miss? But the sect's rules—''

``Hey, take care of this and get out. Are you going to just stand there? This was definitely some trickery, isn't it?''

At that, the two women on either side of Chaeseongha exchanged a glance, seemingly reaching a consensus. They crossed their arms and dragged the culprit away.

``Well, Instructor, should we have another drink?''

``I'll gladly have another. But what's going on?''

``Ah, that?''

Changyo Hong began discussing the affairs of the sect.

The legendary martial arts techniques, the Four Directions Sword, including Zhuque, Qinglong, Xuanwu, and Baihu, which were passed down through battles. The winner of the duel would receive the techniques, but they also had to serve as the sect leader.

``So, let's skip the formalities. We can't just give it away for free, can we? I barely earned this from the old man,'' Changyo Hong smirked.

``So, we'll change things up, and it looks like that's what upset you?''

``Mmm.''

``Well, Instructor. You know I have trouble controlling my temper. But whenever I see you, my anger calms down instantly.''

``Indeed,'' Qing nodded.

The influence of the master's intense training, turning anger management into a fine art.

\textit{I miss Master.}

``If that's the case, then I have no choice,'' Qing said, handing over a combat hairpin.

``Wow, this is heavy. What is this, some kind of spike? Well, I'll see you later.''

Changyo Hong scratched the back of her head awkwardly, but her excitement could be seen as she hummed a tune while walking away.

Qing tilted his head, wondering.

``Instructor, one more drink?''

``Yes, of course.''

The glass kept filling endlessly.

As the night deepened, the academic year at the Yizheng Martial Study Academy officially came to a close.