\chapter{Journey to Diancang (1)}

It seems like this world keeps trying to make me into Princess Yuansui.

But Qing couldn't believe it.

There was a subtle sense of rejection, wasn't there?

Maybe it was because of that damn status window?

If it keeps pushing missions, waking me from my sleep to face danger, with those cryptic writings in the air—interfering in ways that were almost not interference…

Then what about the攻略 (strategy guides) of my past life that I saw?

What about the other parts of the status window?

The missions? My strength and stamina recovery?

The auto-translation from the Korean patch?

Did I really come back to life through the resurrection ritual?

Then, did I perfectly align with that moment?

There was an electronic game in my homeland that had the exact same setting as my past life, and surprisingly, I bought it, installed it, and unconsciously created a character just like the resurrection artist, and then clicked the button to leave the martial world, only to be pulled into my past life's body?

How can I believe this?

So, I'm not in a game, but in my past life, and now I'm the resurrection artist? Oh, okay.

My head isn't full of flowers, and I'm not an idiot who can believe such nonsense.

Qing's expression hardened.

``Alright, let's say it's true. Then, can the memories from my time as the resurrection artist come back?''

``Your Majesty, the memories were already erased in Naraka. There's no way to retrieve them. If I had to explain it, memories were like words engraved on an iron plate. They're like melting metal and reshaping it into a mold.''

Asiya responded while standing upside down.

``Oh, right. It's more like ironware than just an iron plate. The mind was shaped as one lives, but once it's freed from the body and reaches Naraka, it's like being melted into molten metal and returned to its pure form. So, I apologize…''

``Are you saying it's impossible? See, I knew it.''

``Exactly. They're treating me like a complete idiot.''

This world or the status window… it's making a fool of me.

If my body was truly the resurrection artist's body and my soul was his soul, then what? Am I the resurrection artist?

That's just… Ah, I see.

Qing suddenly realized the cause of the rejection.

It's not that I don't believe it; I just don't want to believe it. No, it's not even that.

It's simply not true.

Even if I were the resurrection artist in my past life, so what?

The past me was someone else, not me.

Even if I were reborn, I could never be the resurrection artist.

But the reason I've been thinking about all this, the reason I've been tempted by this wrapped-up illusion, was because of one thing.

The resurrection artist was a good person.

The resurrection artist was loved, and he knew how to love others first.

Maybe it's because the roles reversed. He was someone loved by all because of his kindness.

What if the resurrection artist had been an evil person?

If I were the resurrection artist, and because of him, enemies flooded the world, and all the people spat at me, cursed me, and regarded me with disdain for things I never did?

That would obviously make me frustrated, angry, and upset.

To be despised for crimes I didn't commit and have people attack me for the wrongs of my past life—how could I stand that?

Of course, I'd cut ties and say that I'm not that person.

But the problem is, the resurrection artist was a good person.

He was someone everyone desperately wanted to find. He was loved by so many.

How comforting would that be?

If I just accepted it—''I am the resurrection artist,'' then I could enjoy the rewards of his kindness for nothing.

That's why this whole thing was insulting.

Of course, I am a person who takes what's sweet and spits out what's bitter. I admit that I am petty.

But even so, this… it's ridiculous. Am I supposed to pretend to be the resurrection artist and enjoy the power of the Emperor's authority?

No, it's not okay.

I didn't live that life. Why should I inherit someone else's life just because there's no loss and only gain?

That's just ridiculous.

Meanwhile, the woman who had been persistently trying to hold herself up was now clearly struggling.

Asiya, sweat dripping from her, spoke up.

``Your Majesty… could you please forgive me… this was really straining me…''

``Hm. Forgiveness? I'm not the one to give that.''

``Such mercy from you…''

Qing smiled faintly.

Still, it felt a bit lighter.

At least the real resurrection artist won't be in the afterlife, shedding tears of resentment toward me.

Ah. That's right.

``Then, who was the resurrection artist in the palace now?''

``Well, we just invited the most similar-looking courtesan from the land of Geonpyeong to match Your Majesty's beautiful figure… and it worked out that way…''

``You've managed to keep this secret for so long?''

``Surprisingly, no one suspected it…''

As they worked as palace staff, they were able to gather bits of information about the resurrection artist's past and pretended to be the artist.

No one could have imagined that the princess would be replaced like this.

The person had died and come back to life, so it was possible they had changed.

Plus, they had slowly begun to recall fragments of past memories.

If I heard this, even I might have believed it.

But I am not the resurrection artist.

Because, in the end, I'm not.

And to do that, there was one last connection that needed to be severed.

``Your Majesty, Your Majesty's daughter, the Resurrection Princess, has already died a long time ago.''

The person standing before you was not the Resurrection Artist, but Ximen Qing. Even though it shares the same body and the same soul, it cannot be the same person.

``Why were you acting like you don't know? Why does the watermelon taste bad? It's the end of summer, and the year has had a lot of rainfall, so it's just not sweet.''

``No, that's not it.''

Wrong.

What I should have said to Your Majesty was that the Resurrection Artist needs to be let go, that I am not the Resurrection Artist, that it needs to come to a close.

But I can't do it.

How do you tell a mother who has lost her child, ``Your daughter was already dead, and I am not your daughter''? How do you even say that?

Qing wasn't that cruel.

To be exact, Qing was a very cruel person, but only when it came to people who gave her affection. She was someone who could melt away when it came to those she loved.

``Your Majesty.''

``Yes, my daughter.''

Qing took a deep breath to steady herself.

``Well, what does it mean to exist as one person? Even if it's the same body, if the memories were gone, and the emotions shared were no longer the same—though calling it ‘memories' seems odd—if everything was different, then can we still say it's the same person?''

At this, the Empress softly patted Qing's head.

``Right. It must be hard to accept. But it's alright.''

Suddenly, the mood shifted into an identity crisis.

``That's not what I—''

``Do you know what the last promise you made to me was? You promised that even if you died and were reborn, you would still be my daughter. And now, look, you've kept that promise. You've come back and returned to me.''

``Ah, that…''

``Even I made the same promise. I said that no matter what you were reborn as, I would still consider you my daughter. So there's no need to worry about it.''

``No, that's not it. I'm just—''

``Right. I see. My daughter.''

Hmm. This isn't going to work. This was impossible.

Qing gave up completely.

The Empress had already made up her mind, and no matter how much Qing insisted she wasn't her daughter, she wasn't listening.

Qing couldn't help but laugh bitterly.

Is this how deceptive people can be?

If someone came to you saying, ``You owe me a million gold from your past life,'' would you give it to them?

If it's just a few coins, you'd tell them to get lost, right?

But if they told you that you owed them a million gold from your past life, you'd likely feel guilty and hand it over.

Even if it's not gold but affection.

Perhaps those uneasy elements within me.

Maybe, if I were thrown out of the martial world because of my cursed fate or the Demon Cult, I would feel relieved to have a place to turn to.

But what can I do? I was born deceitful.

Both Haeryu and Deokseong, surprisingly, gave their goodbyes in an unexpectedly plain manner.

``I would have liked to accompany you and serve you, but being bound to the palace like this, please forgive me. Hehe, when you come again, bring the little one with you.''

``Your Majesty. Now that I've seen you in good health, I can die without regrets. Well, I still have some regrets. My lifelong wish was to serve Your Majesty's little one, so next time, please show me the little one.''

The ``little one'' here refers to the royal children, of course.

Though Qing had no intention of bringing Ciyu with her to this treacherous battle, she was still moved by their sincerity.

Unexpectedly, it was Gabiya who made the most emotional plea.

``Your Majesty, the grace you've bestowed upon us will be etched in my heart forever. Please, don't go. I can't live without you. How can you do this to me…?''

Qing was slightly surprised by Gabiya's tearful face.

But it was Gabiya that felt like the most precious bond to Qing.

While Haeryu had sent off the Resurrection Princess, Gabiya was sending off Ximen Cheonhwa.

``Leaving the Resurrection Artist behind, where do you think you're going? You've raised me, you've trained me. I would rather you step on me and go than leave me behind! You can't go, not like this! No, you can't! Ugh, really, really step on me!''

Gabiya collapsed in front of Qing, and Qing gently stepped over her, heading toward the back gate of the Forbidden City.

Traditionally, the position of the Twelve Inspectors was one that was quietly accepted and granted in private, not before the court.

The appointment wasn't even done in front of officials but in secret, by a one-on-one audience with the Emperor, so it wasn't surprising.

And so, Qing finally escaped the Forbidden City!

The air outside the palace felt different.

Was it because the palace air was stifling or oppressive? It was as if the high walls surrounding it made everything feel cramped, like a tightly packed area inside the palace itself.

Still, the countless people who would have to live their entire lives within those walls—how miserable.

It wasn't the palace life for her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ten days later.

The main gate of the Uijeong Military Academy.

Qing had hurried back with some urgency.

But traveling from Beijing to the academy was no small feat.

It was a distance that, if translated to Qing's hometown, was similar to going from Seoul to Busan and back, something like that.

So, when Qing returned to the academy, the sun was still hot, and only in the cool of the evening did a slight chill begin to creep in. It was the beginning of early autumn.

And when news of her return spread, one woman immediately rushed out.

It was an odd time, in the middle of the day when the academic schedule was still in progress, so it was strange for someone to be waiting.

The instructors were busy with classes, the younger students were in their lessons, and Guyeong was playing around. But who would send word to Guyeong?

So why was someone here?

And the person rushing toward Qing, using her internal energy, was someone Qing never expected.

``Eh? What are you doing here?''

``Seriously, what's going on? If you were going to take the instructor position, you should have said something. I would've come much earlier if you'd told me. But I didn't even know about it until later, and now there's no one here! You didn't want to see me, did you? You came all the way here from Sichuan just to see me. How could you be so indifferent to me?''

This was the same person who had been offered the position at the academy but had turned it down with a laugh, saying, `Why would I go there? It's absurd. Am I someone who goes just because I'm asked?'

But now, this person had taken over the academy position, forcing out the previous officials.

It was Tang Lan-Ah, who had finally reunited with Qing.

It was a day just eight days before the academic schedule was to conclude.