\chapter{Journey to Diancang (2)}

As the old saying goes, a true man will change so drastically in just three days that even those closest to him will have to rub their eyes in disbelief, checking again to confirm if it's really him.

That's how fiercely the warriors had been burning with determination. After a round trip to Beijing, over the span of two and a half months, their energy and spirit had changed dramatically.

Though the instructor was away, fortunately, among the academy's swordsmanship instructors, there was a genius in the art of swordsmanship—a man entirely consumed by the sword, Nan-gong Shencai, who had become a sword fanatic.

Qing felt somewhat relieved, knowing that there was a reliable friend like him.

``Has the instructor returned?''

``Has the instructor had a good trip?''

The trainees, who had once been mere novices, had now become disciplined, like a proper fighting unit.

One of the reasons Wulin Alliance had founded the Yizheng Martial Study Academy in the first place was likely to incorporate these warriors into their ranks.

However, Qing couldn't help but feel a bit unfamiliar with the situation.

After all, the warriors had spent two and a half months together, building memories and bonds during that time.

This wasn't just the case for the trainees, but also for the instructors. Naturally, they had become quite close, working together, and after class, immersing themselves in swordsmanship practice. Qing thought, ``When did they get so close?''

Along with them, Gyeongshim, the sharp-witted young swordsman, and Ho-pi-nyeo, the hot-tempered woman, were still swinging their swords with determination after their work hours.

It wasn't exactly an intense reunion, though.

``Oh, you've arrived? Took you longer than expected. You planning to loosen up your body after this long?''

``Huh? No, I'll unpack first.''

``You should warm up first before unpacking, don't you think? I can't understand this.''

In Zhongyuan, reuniting after two and a half months felt almost like not seeing someone for just a week.

In Qing's hometown, a journey that took just one or two hours each way would feel long, but in Zhongyuan, even a trip to the next town would take at least a fortnight.

So, for Qing, a two-month trip to Beijing wasn't that surprising.

But when returning to the Yizheng Martial Study Academy, it felt like stepping into a completely different atmosphere.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As Qing listened to the stories from the young ones, she couldn't help but smile at the playful antics of the children, particularly Ciyu.

``Ugh, it was so annoying. Mom and Mom were fighting over who could sit with me. First, they'd ask, ‘Which mom were you going to sit with?' It was so childish.''

``Who's making you choose?''

``Mom and Mom!'' Ciyu explained, giving a dramatic sigh.

It turned out that after the unexpected forceful takeover of the academy's seat by Dangnana, a petty rivalry had broken out between the two mothers over who would sit with Ciyu, showing just how petty the conflict was.

It was as if two mothers were competing for their child's favor in a way that resembled the age-old ``which parent do you love more?'' question—something even adults would find frustrating.

``Well, that's ridiculous. When were these two going to grow up?''

But of course, that playful teasing didn't seem to help much with Ciyu's emotional stress. No matter how playful it seemed, the children were caught in a storm of confusion and mental fatigue.

It wasn't just a harmless game for Ciyu—having to choose between her two mothers, as if on the verge of divorce, was a cruel dilemma.

But Ciyu wasn't an average kid.

Since she had many mothers, she didn't feel deprived in the slightest. When faced with her own dilemma, she wisely decided to choose a neutral stance.

However, that wasn't enough to stop the relentless tug-of-war. One mother would try to keep her in their lap, while the other would quickly snatch her away.

It was a continual struggle, and as a result, Ciyu was caught in the middle, eating meals on the move, never able to put her feet on the ground after practice hours.

``Let's see. Have you gotten a little rounder?''

``Hehe, it tickles!''

Ciyu had clearly grown a little chubbier, perhaps from eating well and resting properly. Her face glowed with a healthy shine, though her eyes still had the thick dark circles under them.

In the end, the day's activities were finally interrupted by another appearance—Seoliri, determined to steal Ciyu away for herself.

``I wanted to see her. Sob.''

``Huh? Is Guyeong crying?''

``No, it's not Guyeong!''

``Really? Was Guyeong crying?''

``No, it's not that! Not at all!''

Seoliri, with her bloodshot eyes and the clear runny nose that dampened her upper lip, was sniffling and making a stuffy sound as she spoke.

``Got a cold?''

``No.''

``Then what's wrong?''

``A doghouse was a mess, I think. Sniff sniff.''

``Oh, that Lan-Ah.''

It seemed like she'd brought out the poison that completely destroyed the face of the infamous Lady of the Dang family.

``Ah, Qing, were you going to eat? We should eat together. Then, after a long time, we can bathe together. And heh heh, you were badly hurt, right? I really can't live without you. Let me check your pulse. I might have missed something. What if it worsens later? That would be tough. Oh, really. How could you be so careless?''

``Your expression is… hmm, very sinister.''

``What? What do you mean? I'm just worried about you, really. What's so wrong with that? You think checking your pulse was easy? It's a skill, and you can't just fumble around like that.''

``Enough. You used poison on Guyeong, didn't you?''

``No? It's just a cold, I think. After all, you've been around cold air all the time, haven't you caught a cold?''

``Oh please. Stop.''

``No, what were you talking about? Really, Qing, you don't understand. He used some weird technique and made ice cubes in my tea. When I took a sip, it was freezing! Can you believe that? It's completely ridiculous. How could someone make tea like that?''

Making tea cold was considered a grave attack and humiliation in Zhongyuan culture.

All tea must be drunk hot, unless it's fruit tea, which was an exception.

But even with fruit tea, it wasn't really considered *tea*—it was more of a snack.

Likewise, barley tea and other grain teas were not technically considered tea in Zhongyuan, and no one in Zhongyuan would ever drink them cold.

The people of Zhongyuan had an absolute belief that cold drinks were harmful to health and could cause mental instability, leading to madness.

``Huh? With the weather so hot, wouldn't cold tea be better?''

``…? Oh Qing, that's where the problem is…''

``Anyway, friends don't use poison on each other. Quickly reverse it.''

``What? I'm not friends with him.''

``Right, exactly. Not friends.''

``Well, if the parties involved aren't involved, then there's nothing we can do.''

Qing nodded and then spoke again.

``Even family members don't use poison on each other. Quickly undo it.''

``What? Family? With someone like that?''

``No. I don't want to.''

``Well, I'm afraid you don't have a choice while you're playing the role of Ciyu's mom. If you don't want to, stop being Ciyu's mom. Is Ciyu okay with that?''

``Yeah. I have a lot of moms.''

``Ah, Ciyu was lucky, huh? Having so many moms means she can be spoiled. Among her friends, doesn't Ciyu have the most moms?''

``Cheoljeong has seven moms. Some kids have six—Unhwa, Charyeong, and Talbok have three.''

Among the kids, it was a constant competition to see who had the most moms. It had already led to quite an argument among them.

In Zhongyuan, it wasn't considered strange to have multiple mothers, so there was no unusual context here.

After a noisy dinner, Qing finally felt that she had returned to the martial world.

The Forbidden City certainly felt cold and quiet.

It was like everyone was always on edge, and the atmosphere was rather heavy.

I guess I'm just not suited to palace life.

After the meal, Qing spent some one-on-one time with Chunfeng.

``You were appointed as the Twelve Inspectors? That's… well, no matter how much the Heavenly Sword was the next era's unparalleled giant, the only one who can compare was the invincible Heavenly Sword, but now it's really intriguing, isn't it?''

``Next era's unique giant? That would be impressive. But, isn't it just the wisdom of the ancient sages?''

``Heh, of course, that's true. But, to think you'd leave the Forbidden City like this. It's really unexpected. What were your thoughts on this?''

The Twelve Inspectors was, as Qing had expected, a position of secretive inspection, with the right to report directly to the Emperor.

In Qing's hometown, a similar position, called a secret inspector, was only given to those who were willing to risk their lives. It was a dangerous role, often leading to violent confrontations.

But the Zhongyuan inspector was different.

The Emperor's authority was so immense that there was no need to kill someone to silence them.

``Even if they appointed you, I expected it would be for some remote, insignificant position, but to make you the one with real power was unexpected.''

``So, what do you think?''

``Three possibilities. First, the Wulin League might be seeking to make a claim, perhaps to undermine the Imperial Bureau's encroachment. Second, if they're not using hard tactics, maybe they want to pacify the Wulin League by saying, ‘Look, we're assigning someone from the League to such an important position.'''

``And the third?''

``Third, they might covet the power of the Heavenly Sword. They might want to bring it under their control. But that's unlikely. Even if there were no one else in the Imperial Bureau, someone as important as the Heavenly Sword would not be entrusted with such a vital position unless they were exceptional in both skill and intellect.''

``What's going on? Was my finger really that important?''

Chunfeng suddenly hugged his large body and covered it.

Qing, with her left and right fingers straightened, mimicked a gesture that Zhongyuan people wouldn't understand, but it was a humorous gesture nonetheless.