\chapter{Journey to Diancang (6)}

Devouring the Heavens and Earth of Wulin! The previous story.

The most terrifying thing in the world was food.

Therefore, I will erase it from this world.

I will chew it all up, bit by bit.

Ximen Qing, the terrifying serial food ghost Yukhwa, who made all the chefs of the world tremble with her grudge against food, has only one thought in her mind.

Driven by a burning desire for revenge against food, Ximen Qing, who had been slaughtering chefs across the Zhongyuan, finally dared to raid the imperial cuisine of the Forbidden City in Beijing, the heart of China.

But shocking news, an incredible twist!

This terrifying food demon, who eats like a beggar, was actually a noble princess of the royal family!

However, consumed by her intense hatred for food, Ximen Qing, far from maintaining the dignity of her noble lineage, shocked the entire palace with her subhuman eating manners.

Even the Emperor, full of paternal love, turned pale at her horrifying table manners and endless appetite.

Finally, the Emperor declared:

``You, who were like a pig, were not my daughter.

And the imperial cuisine was tasteless. I will give you a special guest pass that allows you to eat anywhere without waiting in line, so please leave the palace.''

Thus, Ximen Qing, the gluttonous food demon who had devastated the imperial food stores with her brutal massacre, safely returned to the Wulin world!

From the perspective of Wulin, it might be quite regrettable.

Having chewed up all the unfinished meals at the Uijeong Martial Arts Academy, Ximen Qing now turned her gaze towards the remote lands of Yunnan.

In every city she passed through, the cries of gratitude from the waiters and cooks who had lost all their goods to sell were drowned in tears, as a terrible flood of destruction followed.

From Namsuhyeon in Henan to Deokjuhyeon.

Entering Hubei, passing through Nohagu-hyeon, Yangban-hyeon, Namjang-hyeon, Heungsan-hyeon…

Finally, she reached the front yard of the Divine Maiden Sect, more famous as a sanctuary of beauties than as a mysterious martial arts sect.

At this moment, a righteous group rose up, declaring they would stop the endless food massacre of the food demon Ximen Qing.

Finally, in the grand banquet hall of the Seolga Trading Company in Jagwi-hyeon, a mountain of food was piled high on a super-large dining table, and a challenge was thrown at Ximen Qing: ``If you can eat it, then eat it!''

``Ugh, I'm so full. I'm really going to burst.''

Qing said as she scooped up a split fig (surprisingly, figs were called figs even in the Zhongyuan) with a spoon and ate it.

The group's gaze alternated between Qing's bulging belly and the mountain of figs piled as high as a person on the table, as well as her busy hands splitting the fruit with her nails.

But Qing was unashamed.

Fruit was fruit, not rice.

Therefore, no matter how full you are, you can eat it, and it aids digestion, was good for health, and doesn't make you fat.

Isn't this an undeniable truth guaranteed by all the mothers and grandmothers of the world?

``Ah, Gramps. I'm going to sleep here today.''

``Why are you sleeping here? I thought you considered this place just a restaurant. You were always in a hurry to eat a meal and leave.''

``Eyy, Gramp. I said I'm going to sleep here.''

``You only sleep here when it suits you. Tsk tsk.''

Choi Riong said this, but he couldn't hide the slight curl of his lips, an unavoidable reflexive reaction.

Perhaps it was because of the child who had buried her head in the old man's shoulder and slumped down.

In fact, she hadn't walked much on her own, so why was she so tired? Of course, children were like that.

The child, who had been dozing off while eating, made Choi Riong's eyes flash.

Finally, he was enjoying the ultimate luxury of his later years, cradling his granddaughter (to him).

Although grandpa had become more generous than before, he still looked so happy, so it was just a matter of staying one night.

Originally, the reason for eating dinner at the Seolga Trading Company and then going up to the Divine Maiden Sect was that she couldn't loiter in the front yard without paying respects to her master, so since he wasn't here now, it was fine.

After eating a hearty dinner, Qing went to find Seolga, the highest intellect among the three stars.

Seolga was now a beauty.

A tall, handsome beauty who looks like she would be good at sports.

However, with her bold appearance, she was engrossed in sewing under the lamp, which somehow didn't seem to fit.

But the thing she was diligently sewing was an artificial chest, a secret manual of divine combat.

``What is it? Has cross-dressing become your hobby now? Have you finally reclaimed your gender identity?''

``Don't say such terrible things. It's just work. Work came up.''

``Huh? Another beauty scheme?''

Seolga smiled wryly.

``Men are like that. Their brains were attached to their dicks, so they can't think straight when they see a woman. You know that, right?''

``I've seen a lot of those bandits.''

``It's not about stabbing with a sword. You know, men want to stab women—''

``I know, right? You think I think you're a bandit who wants to stab with a sword?''

``Ugh, at least act a little embarrassed.''

It was a natural tease, as usual.

Of course, Qing was immune.

``So, what did you come to ask this time? I don't know why you keep asking this illiterate guy when you have the Zhuge family.''

``Illiterate? If Seolga is illiterate, then the savior of the world is a monkey. Modesty is one thing, but this is too much. The highest intellect among the three stars shouldn't say such things.''

``What kind of half-baked nonsense is that?''

``Anyway. Half-sword demonic calamity, Heaven-shaking laughter, Heaven-reversing blood-heart finger technique—what is this, so long? Do you know anything?''

Seolga's expression hardened.

Previously, she had come every night to ask at the Tianshan Divine Market, and after that, a blood calamity arose, and she became a vicious woman who learned martial arts.

``Even so, you should at least refrain from the Ten Great Demonic Arts. And why those three? They're all crazy.''

``Crazy?''

``Here, here.''

Seolga tapped his head.

And with an exasperated expression.

``……If you don't know, just say so. Don't make that face. Your only advantage is your peerless beauty, and if you make that face, what will happen?''

``It's really unfair to hear that from Seolga. Seolga is a three-star intellect and also a peerless beauty, so I can't compare. Wow, I feel so shabby. I'm only the youngest Hwajung? I have nothing to boast about…….''

``Ahem. Well, people.''

Seolga shook his head gently.

Even the highest intellect among the three stars, Seolga, couldn't stand against the wicked tongue of Qing.

``I'll tell you what I know. The Dao Demonic Calamity is a martial art that feeds people to create a demonic sword and wields the martial artist, not the other way around. What do you think happens when a person is wielded by a sword?''

Qing wasn't curious about what kind of martial art it was, but where it was and if he knew any demonic heads that had mastered it.

But she was curious, so she listened.

The Heaven-shaking Laughter, also known as Heaven-shaking Sound, was a sound art that confuses the mind and shakes the insides with a loud laugh.

It doesn't have grand effects like blowing up heads with laughter, but if you have the lung capacity, you can laugh throughout the fight and gain the upper hand.

However, the problem was that such an evil laugh cannot come from a sound mind.

The more you master it, the more you become a madman.

``The Heaven-reversing Blood-heart Finger Technique is a Qi Cultivation technique, and I heard it reverses Inner Qi. So, from the dantian, it goes up through the Ren meridian to the upper dantian, then down through the Du meridian to the perineum. Hmm. Perineum. Do you know where your perineum is?''

``What, are you a ten-year-old kid? Obsessed with the perineum acupoint?''

For reference, the perineum was between the legs, precisely between the genitals and the anus.

``But reversing Inner Qi? Does that make sense? You'd immediately fall into Qi Deviation and go mad, right?''

``That's what I said. It's crazy.''

Does it make sense? No.

You'd fall into Qi Deviation and go mad, right?

Actually, they do fell into Qi Deviation and go mad.

``So, what happened to those crazy guys? Did they appear somewhere?''

``Those who are properly crazy don't stay quiet, so if they appear, rumors will spread quickly. But have you heard any?''

``I'm not really into rumors. Seolga, you go to the upper levels a lot, so you must have heard things here and there.''

Seolga let out a deep sigh.

``If you really want, I'll look into it.''

``But don't go around asking too much. If rumors spread that the Seolga Trading Company is looking for the Ten Great Demonic Arts, what would happen?''

``You know that, but still looking…whatever. You must have your own thoughts. Hmm. You must have thoughts, right? Yeah, you must have thoughts.''

``It's true that I don't have thoughts, but you don't need to emphasize it so much, do you?''

``I think I need to emphasize it…''

Because no matter how much you emphasized, it's never enough.

Qing just asked casually, thinking that since Seolga was a big trading company, they might be sensitive to rumors, and since Seolga was the highest intellect among the three stars, he might have heard something.

But to the members of the Seolga Trading Company, it was different.

The Supreme One has commanded!

It was the glorious command of the Supreme One!

Half-body Demonic Calamity! Heaven-shaking Laughter! Heaven-reversing Blood-heart Finger Technique!

Find them! Search the entire world if necessary!

The devout followers of the Divine Cult, who had been quietly engaged in their livelihoods, burned with enthusiasm under the stern command of the sage who had descended to the mortal world.

The next day, for some reason, the Seolga Trading Company was eerily quiet.

``Hmm. Isn't it a bit empty?''

Normally, when you walked around the Seolga Trading Company, you would encounter employees eagerly sharing their snacks, so although she didn't particularly want to receive any, today it felt unusually quiet.

``Umm. Is it usually like this? It's only crowded when Xiao-mei comes, and usually it's like this.''

Gyeonpohee's response was affirmative, but the ``Umm'' meant no.

She heard that usually, the Seolga Trading Company wasn't very crowded.

After eating breakfast, she went up to the Divine Maiden Sect with Jin Jangmyeong.

``Has Grand Junior Master arrived? Junior Master Chen too.''

``Ah, but where is Ciyu?''

``Ciyu is at the foothills. I'm planning to pay my respects to the Sect Leader and then go to Yunnan for a bit.''

``Wow, you're leaving again right after arriving?''

For some reason, the main gate of the Divine Maiden Sect was calm.

Without the usual noisy chatter, it felt empty and like something was missing.

Because those two weren't here.

``Hmm? But where are Siliang and Lianshu?''

``They were on duty from yesterday afternoon until night. They had a feeling Taesasukjo would come? But I guess their feeling was off. They're probably sleeping now. Should I call them?''

Actually, it wasn't a feeling; they had received Qing's visit date in advance through the Seolga Trading Company's food supply connections.

But this time, Qing came to sleep, so.

``No. They're on duty and sleeping, so there's no need to wake them. I'll see them later.''

Qing stopped by the dormitory to tidy up her clothes and then headed to the main hall.

She paid her respects to Wang Juhui, the sect leader of the Divine Maiden Sect, who now had a dignified presence befitting her nickname ``Heavenly Thunder Sword.''

After staying for a while, she looked around at the disciples and enjoyed a hearty meal of the Divine Maiden Sect's delicious food.

Then, Qing left the sect again.

She would have liked to rest at home for a few days, but well, since she had to go, she might as well go quickly.

``Take care. Don't stay too long.''

Chen Changming saw her off.

Unfortunately, Wang Juhui did not allow Chen Changming to leave continuously.

After all, she had been away for more than a season.

'If you keep wandering, when will you train?'

'Or at least reach the level of a supreme master like someone else?'

If it's unfair, there's no choice but to become a master.

Thus, Qing finished her short return home and set out on the martial world journey again.

About 4,500 li remained to the Diancang Sect.
