\chapter{Journey to Diancang (7)}

Understanding the Zhongyuan' Terrain, Part One.

The west was high, and the east was low.

This elevation difference isn't a simple concept where the further west you go, the higher it gets.

Roughly speaking, if you take Uichang County, three hundred li east of the Divine Maiden Sect, as the boundary between east and west, the west was blocked by endless towering mountains, forming a rugged mountain range like a high wall.

This elevation difference might be hard for people from Qing's hometown to understand.

To put it simply, if someone living in a city on the western mountain range and someone from the east wanted to match heights, how would they do it?

They would need to stack five of the 63-story Yeouido Iron Towers, a traditional and ancient Korean architectural relic, vertically and stand on top of them.

And even that was only if we're talking about Guizhou, the weakest of the plateaus. To match the elevation of Yunnan, you'd need at least eight of those towers, and for Qinghai, at least twelve.

So, in the past, when Qing decided to take the shortest route and run straight through Zhangjiajie, it was truly a foolish and ignorant act.

But Qing could afford to do that.

If your body was strong, you don't need to use your brain.

However, now there's no need to rush as much as before.

And with the group including weaklings who were almost no different from ordinary people (it's hard to consider Dang Lan-Ah, Zhuge Yi-hyeon, and those below the peak as true martial artists), they had no choice but to take the easier path.

``Attention, boat owners! We'll take you to Changsha by boat. We'll board the boat with the best conditions!''

A woman with her face covered appeared at the rapidly developing port of Jagwi County and started spouting nonsense.

She said she'd take them by boat?

And not just any boat, but the best one she could find based on conditions?

But that was only for a moment—

``Boat owners, here's the Dragon King Token!''

The Dragon King Token has appeared!

The boat owners' heads turned in unison, their eyes gleaming with excitement.

The Dragon King Token was a miraculous item that completely exempts one from the Yangtze River toll, the only way to avoid the terrifying taxes that were even scarier than natural disasters.

This changed the story, as it was a great fortune that could wipe out the soaring tolls in one go, depending on the size of the boat, cargo, and passengers.

Of course, they could have taken a merchant ship from the Seolga Trading Company.

But if they asked the Seolga Trading Company, it wouldn't be just a casual ride; they would mobilize a top-class passenger ship just to take Qing, which would be a bit too much.

They could just hitch a ride on any boat heading that way, no need to go to such lengths.

So, they boarded a boat to Changsha, the capital of Hunan Province.

About 4,000 li remained to the Diancang Sect.

From Changsha, they could rent a carriage and follow the official road.

The road was laid out along gentle mountain paths, so even as they climbed and climbed, the endless uphill road stretched before them.

But with a carriage, it didn't matter.

Am I tired? No, the horse was tired.

So, riding the carriage along the bumpy mountain road for 2,000 li, they finally reached Guiyang, the largest city in Guizhou Province.

And thus, Guiyang!

Surprisingly, there's nothing here!

Well, Guizhou was the countryside of the countryside.

If you ask people from the Zhongyuan which part of the Zhongyuan was the most rural, eight out of ten would point to Guizhou.

The other two would point to Guangxi.

You might think Qinghai and Yunnan were even more remote, but Guizhou was still considered part of the Zhongyuan.

The areas further west, like Qinghai and Yunnan, and further east, like Liaodong and beyond, aren't even considered part of the Zhongyuan, so they don't count as countryside.

So, Guizhou was in an awkward position.

Guizhou was awkward.

The weather was mild year-round, with summers not too hot and winters not too cold, but it's not exactly summer or winter weather either.

The scenery was pleasant enough that you won't get tired of it, but it's not exceptionally beautiful.

There were no famous must-see scenic spots, so tourists don't particularly visit this rural area.

Moreover, unlike Qinghai or Yunnan, it doesn't boast the exotic lifestyles of ethnic minorities.

But being considered part of the Zhongyuan means it has been integrated into the Zhongyuan for a long time, with Zhongyuan culture and customs deeply rooted.

Even its specialties were ambiguous.

If there's a specialty, it's Guizhou tea, but neighboring Yunnan Province was the hometown of the best tea in the world.

However.

At the Guiyang's best inn, Jianling Pavilion, a hot atmosphere swirls despite the cool weather.

Sweating profusely, breathing heavily, drooling, and yet completely engrossed in eating, failing to hold back exclamations of amazement.

``What on earth is this taste…!?''

``Sweat is pouring, my mouth is on fire, and my heart feels like it's about to burst! But I can't stop!''

``Sssss, I need more alcohol! Hey, waiter! Bring me a bottle of Maotai, no, a whole jug!''

``Oooh, my chopsticks won't stop moving!''

``Ahhh, what is this! Sssss, how can such a taste exist in this world! This is the best taste of my life! What on earth is this taste?''

``Don't you know? Ah, this is what we call 'spicy.' It's loaded with chili peppers.''

``Spicy! This taste is…!''

``Spicy! So spicy! Too spicy! But I love it!''

Qing's eyes sparkle as she comes down to eat after unpacking.

\textit{Oh, spicy food seems to be famous here?}

``Is spicy food famous here?''

``In Guizhou? I haven't heard of it.''

Zhuge Lixian frowned.

Chili peppers, that mysterious red spice that had quietly made its way in from somewhere, hadn't yet spread widely.

But if Qing were well-versed in Zhongyuan history, she would know that Guizhou wouldn't become famous for spicy food for another hundred years.

And she would also know that this was the time when the legend of the Zhongyuan' spiciest flavor was born.

Later, it would be said that Sichuan people aren't afraid of spicy food, Hunan people don't care about the level of spiciness, and Guizhou people were afraid of non-spicy food.

This was the beginning of Guizhou people's love for spiciness!

Of course, Qing was ignorant of Zhongyuan history, and at least in this regard, you can't blame her for being ignorant.

Who among all humanity in the world would care about the history of the Zhongyuan?

It's only natural not to know the history of the Zhongyuan; those who know it in detail were the strange and suspicious ones.

``If we're talking about Guizhou's specialties, I've heard that the local liquor, Maotai, is quite good.''

``Ah, Maotai?''

Qing's ears perked up.

Maotai. In Zhongyuan pronunciation, it's Maotai liquor\footnote{茅台酒; Maotaijiu}.

\textit{Isn't that a super famous liquor? The most expensive liquor in the Zhongyuan, right?}

Well, not yet.

Maotai wouldn't become the Zhongyuan' top liquor for another two hundred years.

Qing's eyes sparkled.

\textit{Liquor is good, but spicy food!}

\textit{It's been so long since I've had properly spicy food in the Zhongyuan.}

Of course, spiciness existed in the Zhongyuan.

Besides chili peppers, which Qing was familiar with, there were a few other spices that could create a spicy flavor.

But the fiery sensation from chili peppers was a new experience for the people of Guiyang, as it had never been felt before.

Qing's spiritual roots were Korean.

And when you think of Koreans, you think of spicy food.

Of course, the ancestors of Koreans might feel wronged.

They might even yell in protest.

'What nonsense was this? Our people didn't eat spicy food historically, so how did spiciness suddenly become our flavor? 

But at least by the time Qing entered Wulin, Koreans loved spicy food!

``Waiter! Is spicy food famous here? Is it very spicy?''

``Haha, sir. It's not exactly famous yet, but it will surely become famous in the future. Last year, our chef, Yi Sai, tasted the Mala Ultimate Soup from Sichuan, claiming to be the best chef in the world, and was shocked.''

``Oh, Mala Ultimate Soup. That was delicious.''

``Tsk tsk. Sir, you don't understand taste. Chef Yi Sai was shocked because such a fiery chili pepper was used to make such a mediocre dish. How can that even be called cuisine? It's just a pot of soup sold on the streets.''

``What!? How dare you insult Mala Ultimate Soup? This is an insult to me! I can't stand it!''

``Lan-Ah, calm down.''

``If Qing says so, then I guess I have to… ''

Lan-Ah, who had flared up, was quickly subdued.

``Ahem. That was the fateful meeting between our chef Yi Sai and chili peppers.''

Chef Yi Sai, who fell in love with the taste of chili peppers, took the seeds and started growing them himself.

So, naturally, the chili peppers grown here were much spicier than those from Sichuan.

``Therefore, even if you go to Sichuan, you won't find spiciness like ours.''

``Hmph. How spicy can it really be?''

Sichuan had been a stronghold of traditional spiciness even before chili peppers, so the waiter's pride in spiciness didn't sit well with Tang Lan-Ah.

``It sounds delicious. Then, half spicy and half not too spicy. About ten dishes. And for liquor, Maotai and anything better you have. What about the rest of you? What will you eat?''

Ten dishes make for a big spender.

``YES!!! HERE!!! TEN DISHES!!! SPECIAL YI SAI SPICY PORK!!! LOVE TOFU!!! CHILI CHICKEN!!! AHHH, AND… ''

The waiter shouted the dish names loudly as he left, and Qing swallowed her saliva, looking forward to some proper spicy food after a long time.

戀愛豆腐果. Lian'ai Doufu Guo (Love Tofu\footnote{Yes, it's its real name}).

Looking at the spicy tofu pancake, which would later become a representative dish of Guizhou, Qing tilted her head.

\textit{What's this? It doesn't look that spicy.}

So, she took a big bite and chewed.

``Gahk. Ugh, gahk…!''

The fiery chili peppers stuffed inside the tofu set her mouth on fire.

It wasn't just spicy; the chili peppers were crushed and pickled in vinegar, creating a sourness that shot up her nose, and it was incredibly spicy.

It was a spiciness she had never experienced before.

``Wow, sssss, what is this, sssss, how can this be, wow, sssss.''

``What? Is it that spicy? Oh, it's spicy.''

``It's spicy, but is it worth making such a fuss?''

``Oh, Sister. This is really fiery.''

That was the evaluation from Dang Lan-Ah, Peng Daishan, and Zhuge Lixian.

Xue Iri wasn't interested in anything but hot soup, and Jian Buxi just tilted her head, watching Qing struggled with the spiciness.

``Sssss, why aren't you guys, sssss, ugh.''

Qing was shocked.

\textit{Me! Of all people…!}

\textit{I can't handle spicy food!?}

\textit{This can't be!}

Qing's spirit was Korean, but her body was from Zhongyuan.

And spiciness wasn't something you endure with willpower or preference; it's just in your genes, your body.

Yuansui's body couldn't handle the unprecedented intensity of the spiciness.

In fact, until now, the spiciness in Zhongyuan was more numbing than fiery.

``Ugh, there's spicy food, but I can't eat it.''

``Xiao-mei, are you crying?''

``No, I'm not crying. Sssss, it's just that my eyes were watering. Sssss, Ciyu, don't eat it. Yi-mei, children shouldn't eat this. If you eat something too spicy, you'll really suffer. Sssss, it's deadly.''

``Okay… ''

But.

``Ugh, sssss, it's so spicy, ugh ugh. Sssss, wow, it's deadly, ugh.''

Qing's stomach was invincible. It had to be invincible.

There should be no food in the world that Qing cannot conquer, so the current suffering will turn into future pleasure.

\textit{Too spicy? That's just weak talk.}

\textit{Spicy food is training; the more you eat, the higher your spice tolerance becomes, right?}

\textit{Do people who love spicy food eat it from birth? Did they suck on spicy baby formula or something? It's all about willpower.}

\textit{If you don't put in the effort to eat it, of course, you won't enjoy it. Spicy food is so delicious. Ugh ugh.}

\textit{Even though I've lost all the precious spice tolerance and experience I've built up over the years. Sssss. Ugh, it's so spicy.}

\textit{What's lost can be regained. Ugh ugh.}

The group's expressions as they watch Qing were pitiful.

'If it's too spicy, just don't eat it. Why are you eating it while crying?'

Thus, Qing accepted her identity as someone who can't handle spicy food but didn't despair and strived to overcome it.

Which was more admirable: being born able to handle spicy food or overcoming a weak constitution through great effort?

It was a lesson in the proper attitude toward spiciness that everyone should follow.

Anyway, after shedding sweat, tears, and drool over the long-awaited spicy food.

After a good night's sleep, more sweat, tears, and drool in the morning.

To others, it looked like she was possessed by a ghost.

Maybe the ghost of someone who died from eating too much spicy food.

Although the schedule wasn't urgent, there wasn't much to see for sightseeing.

There were famous temples and pretty mountains, but.

The temples in the Zhongyuan were more impressive, and the mountains in Yunnan were prettier.

So, they left the boring city of Guiyang early and headed for Kunming, the capital of Yunnan Province.

About 2,000 li remained to the Diancang Sect.