\chapter{Journey to Diancang (3)}

''This Sima-lang was just stating the facts, nothing more? The position of the Twelve Inspectors was not something to be taken lightly.''

The Twelve Inspectors were the last line of conscience within the Imperial Bureau and a minimal safeguard for Zhongyuan's rule.

It's due to the unique structure of the Zhongyuan administration, which was distinctively Zhonghua in its governance.

Basically, once you take up a position in the administration, the base salary was extremely low.

Unless you're living in extreme poverty (like a beggar), the salary was barely enough to maintain the basic dignity expected from the position for you and your family.

So, what about the rest?

You have to take care of that yourself.

But how many officials in Zhongyuan live in poverty?

Most of them live comfortably in vast estates, with all their power and wealth coming from what they personally acquire.

The problem, however, was that this was illegal.

They have to rely on powerful backers to maintain their positions, exploit the common people's share, and make the rich richer while the poor stay poor and continue to suffer.

Which country in the world would enshrine such laws?

In other words, no official in Zhongyuan was free of guilt!

So, saying that there were no decent people in the Zhongyuan bureaucracy might not be far from the truth, but still…

And in Zhongyuan, any crime committed by an official was a huge scandal. Even the smallest wrongdoing becomes a major crime if the Imperial Palace decides to intervene.

Therefore, the Imperial Palace can easily have any official killed at their whim.

Not just the official, but also their entire family can be executed for committing such a ``great crime.''

This system helped Zhonghua maintain its strong centralized government despite its vast size.

Amazingly, this ``Zhonghua'' method still exists, where the corruption of every official was allowed and even encouraged, creating a system where, when the emperor wants, they can purge any official at any time using the power of death.

Thus, the Imperial Palace doesn't need to actively try to root out corruption—it's almost as if they turn a blind eye and let it happen, because the more corrupt the officials are, the stronger the ruler's authority becomes. Meanwhile, the people suffer, but what can they do?

This was the very essence of the Zhonghua mentality.

Strangely enough, this system was still in place in Qing's homeland, inherited as the ``Zhonghua Spirit'' and maintained as a traditional and efficient system of governance.

Thus, the position of the Inspector was the last conscience of this ruling system, the final safety net to prevent a rebellion.

While the Inspector doesn't usually go around executing those who need to be purged, they do play a role in warning others. If someone crosses the line, they'll step in and say, ``You've gone too far. You better stop, or next time we'll bring out the execution block.''

Hmm. Sounds like the country's in chaos.

But in Zhongyuan, there's the terrifying legacy of the First Emperor, who left behind the cruel curse of Zhonghua—a curse that, if the empire breaks apart, could cause disasters that would never be seen again.

They're lenient toward the barbarians but insist that the land of Zhongyuan must remain unified, an absurd belief.

The Emperor was the sacrifice to stop this curse.

The idea of the Emperor ``ruling'' isn't entirely wrong either.

The Emperor himself doesn't seem very happy about it.

``So even for this Sima-lang, it's difficult. What exactly was the Imperial Palace scheming? But based on past precedents, when the first Heavenly Sword starts using the power of inspection, it's highly likely that it will be used as a justification for attacking the Wulin League.''

``Mm.''

However, Qing's thoughts were a bit different.

After listening to Chunfeng's explanation, Qing thought she had begun to understand what the Emperor's intentions might be.

When the Wutian Great Master grabbed the Emperor by the throat and shook him, didn't the Emperor say something like, ``Then you become the Emperor''?

Wasn't the current Emperor in a similar situation?

Qing, speaking on behalf of the Wulin League, would say the country was in chaos, and that the righteous sects were contributing to the peace of Zhongyuan.

Had the officials been ruling the people well, the Wulin League would have been considered popular heroes, but since the righteous sects were following the path of justice, there's no need to interfere with them. The Emperor would likely agree and say, ``Fine, here's the power of the Twelve Inspectors, go deal with the officials.''

But the Emperor's true intent was still unclear.

Was it a cold sarcasm from the Emperor?

If it were possible, they would've done it already. But since it's not, this was the alternative.

The Emperor was simply trying to hold Zhongyuan together, a position he had to survive in. It wasn't a position of supreme power, and anyone who had actually tried to manage the country would understand the burden.

Qing suspected the Emperor's thoughts were closer to the first interpretation.

However, according to Princess Haryeon's argument, the second interpretation could not be completely disregarded.

``Hmm, I don't really know.''

If you're unsure, it's best not to do anything, right?

Honestly, I don't know either, but as long as I can keep myself and my loved ones safe, that's all that matters.

What Zhongyuan people do was none of my concern.

But, if the Imperial Bureau does something terrible, I now have the legal right to cause a ruckus. In that sense, it's like receiving a great gift.

``By the way, would you mind preparing a speech for the closing ceremony?''

``Huh? Me? What qualification do I have…?''

Qing scratched her head.

The instructor came back, but it was like he had done nothing. After being away for the entire academic schedule, he finally returned with personal matters on his mind.

``This Heavenly Sword… First of all, the praise for someone like us, a special existence, someone you can hardly consider a regular person—it's a form of admiration that, to the common people, becomes a lifelong achievement they can proudly boast about. This was what gives them the strength to walk with their heads held high for the rest of their lives?''

``You've been thinking about this ‘someone like us' thing for a while, haven't you?''

``Objectively speaking, the achievements of the swordsmanship academy were outstanding, and it's traditionally the instructor's role to give the closing speech, don't you think?''

``Well, it's not that I did well—it's more like the trainees worked hard, since I've been away for so long.''

``Heh, this Heavenly Sword. Humility was a virtue of the common folk. But for someone like us, it only brings out the jealousy and inferiority complex of those beneath us—like poison, you see? The Three-Tiered Sword technique you created astonished even the military of Meng, and it's not only a brilliant training sword but also an outstanding combat sword with profound depth. That alone qualifies you to give the closing speech. In fact, from now on, the position of the closing speech at the Yizheng Martial Study Academy should be permanently yours, Heavenly Sword.''

The blatant flattery made Qing feel uncomfortably hot in the face, making it hard to just accept.

``I didn't make the sword technique by myself—Geongu and Murong Soje helped too…''

``A true leader gathers followers and guides them with their fingertips to achieve results. That was the destiny of those like us, born to lead the inferior. So the Three-Tiered Sword, without a doubt, was your creation. No need to remember the names of those ordinary people.''

Sama Chunfeng's inherently kind nature meant he viewed helping others as his duty, and it was fortunate for Qing, or he might have ended up like some moustached dictator who never would've even been born in this world.

Qing replied with a slightly awkward expression.

``Well… I guess. Shouldn't I actually be thanking them for helping me create the Three-Tiered Sword?''

``Heh, finally, Heavenly Sword, you're starting to understand my position a little, aren't you? So, will you prepare the closing speech?''

``No, let Sama do it. Since I've been away for so long, it feels a bit off for me to do it.''

Even so, the closing speech felt a bit much.

Sama Chunfeng looked at Qing with surprise.

``Me? But, as the one responsible for running the academy, I do have enough qualifications, don't I? I could say that if anyone should do it, it should be me.''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The level of the trainees had clearly improved, so Qing found that there wasn't much left to correct them on, unlike before.

With the end of the academic schedule approaching, Qing felt a bit conflicted.

Going to the palace had caused a mess, but at least now she could definitively say she was no longer Yeoonsul.

Moreover, she had learned that the Imperial Palace wasn't a group of purely evil people, but rather a terrible ruling class that had never cared about the common people.

She had also gathered a lot of information from the Temple of the Celestial Maid and had learned some advanced techniques, though she still felt like she had wasted a lot of time. The real issue was that when she visited the Forbidden City, she wasn't Ximen Qing, the Wulin hero, but still in the role of the Resurrection Princess.

Even after the betrayal—or what felt like a betrayal—by Ban Yakgong, she didn't feel angry or upset.

After all, she was not Yuansui.

It was just some old man pretending to be friendly, only to suddenly pull out a knife.

The real turmoil for Qing came from the realization of how weak and powerless she had been when facing such powerful martial artists, particularly those like the Wulin elite who could easily defeat even a transcendental warrior like herself.

She knew the Wulin experts were monsters, but she hadn't anticipated how helpless she would feel in front of them.

Apparently, Ban Yakgong's martial arts were based on the Heavenly Tai Chi, a style that focused on receiving and deflecting attacks, relying on defensive techniques to protect oneself.

If it had been a more aggressive martial style, it would've been incredibly dangerous, and Qing might've been injured far worse.

Luckily, she hadn't been sliced to death, just narrowly avoiding injury. The defensive technique, however, left her no room to retaliate—she had no choice but to run.

Despite this, Qing had managed to endure the constant attacks from the many palace guards and even managed to break through some of their defenses.

Had Ban Yakgong studied a more offensive martial art, there might have been a chance for them to clash swords, but what would have happened if she had faced a true monster like the Wulin elite?

The elderly man hadn't even known that they were facing Wulin warriors, and there were likely many more such monsters hiding in the shadows.

Ximen Sulin had warned her, but experiencing it firsthand made her realize just how terrifying it was.

However, in order to reach that level, she still had a long way to go, and the time had come for her to gather strength.

She needed strength! Massive strength!

One option was to complete the creation of the Dokogukgeom, the legendary sword technique that Ban Yakgong had flinched at in fear.

That was just a pale imitation of the original Three-Tiered Sword, but it would still be a good start.

For now, the goal was to gather the rest of the foundational techniques as quickly as possible.

Mucheondaeje had once recommended the point-chang method, so perhaps when her master wasn't around, she could head to Yunnan's point-chang school.

And then…

Qing opened the mission panel.

She only opened the mission panel when it was convenient.

\begin{quote}
	Ultimate Martial Art: Northern Myeong Divine Power.

Gather all the Ten Great Martial Arts, learn the Ancient Pulse Flow technique.
\end{quote}

The techniques listed were far from easy.

Qing had already mastered seven of the Ten Great Martial Arts, leaving only three left to be learned.

Even if she exchanged for points, it would still be impossible to gain all of them.

But at least two could likely be exchanged—if she didn't do that now, she might lose the chance later.

The Ten Great Martial Arts would need to be actively pursued from here on out.

If she found the right opportunity, she had to take it.
