\chapter{Ximen Qing (again) (2)}

"Speak in detail. In the utmost detail."

"About that, the Demonic Cult's Advance… Wave? Labor Brigade?"

Qing cocked her head.

\textit{Ehhh? Was it actually a combination of the two? Something Something Brigade? But it kinda seems right?}

Qing tried to recall the memory.

Meanwhile, Ximen Surin was horrified.

It was understandable since the very beginning of the sentence had already taken Ximen Surin's breath away.

"Demonic Cult! Those damned evildoers!"

"They were really bad guys, I think."

That was correct. In fact, there wasn't a single one among them whose Evil Karma was low.

It was said that the Demonic Cult was a gathering place for bad guys. And apparently, that information seemed rather accurate.

"That happened when I, mm, entered some city. There, this granny……"

Qing naturally skipped over the name of the city.

After all, reciting specific proper nouns that were just heard in passing was a trick only protagonists in novels could do.

For the same reason, though Qing recited a grand, heroic epic about acquiring a flute, people's names were strangely omitted.

However, the storyteller's subjective interpretation was somewhat mixed in as well.

The Indomitable Advance Labor Brigade of the wicked Demonic Cult!

Qing alone blocked the enemies in a decisive short-term battle, just like Zhang Fei in the Battle of Changban\footnote{In the novel Romance of Three Kingdoms, Zhangfei stand alone on the Changban bridge, making the pursuing Cao Cao's force retreat in fear. But in the historical collection Records of the Three Kingdoms, the bridge was already destroyed by Zhang Fei and his men beforehand. He still mocked the pursuing enemies on the other side, though}, and took their heads.

Then, the puppets of the wicked Demonic Sect wet themselves in fear and fled.

Thus, Ximen Surin's disciple pursued the enemy in a phenomenon similar to storm and gale.

Upon finally facing the enemy's leader, she intended to finish off the evil tomb robbers.

As such, she took the head of a Transcendent Realm ene…….

"So, the Captain of a Demonic Cult combat unit was at the Transcendent Realm? I have not heard the name of Advance Labor among the elite brigades, though."

Qing flinched.

\textit{Ah. So she knows the combat units of the Demonic Sect, huh?}

Qing switched up her words.

"He wasn't exactly at the Transcendent Realm. So like, he was at the really, really, really Late Stage Peak Realm which was basically no different from the Transcendent Realm…….?"

Qing's guilty conscience made her twist the story from a heroic tale to a kind of memoir.

She included the scene where, when offered to spare only one, the enemy immediately stabbed his own boss in the back, showing no loyalty whatsoever.

"Indeed, those scoundrels of the Demonic Sect are like that. Oho? Disciple's performance was truly excellent! That is right, it is time for a renowned female martial artist to emerge as a hero in Jianghu!"

Ximen Surin was very pleased.

It was a bit awkward for Qing to genuinely share in the joy, though.

"However, Disciple's achievements are still quite modest, so it seems that it is not yet time to raise the value of your name in Jianghu…"

"But still, that very disciple is at the Late Stage Peak Realm…"

"Is it not merely the Late Stage Peak Realm? In a world where any martial school in a city of considerable size has a Peak Master, how could Disciple be so frail, delicate, and sickly…"

It would be a sorrowful thing to hear for the Peak Masters of Jianghu.

If a twenty-year-old girl was considered frail at the Late Stage Peak Realm, then those who were happy to just reach the Peak Realm at the age of fifty should reflect on themselves with tears streaming down their faces.

But that didn't mean she was wrong.

After all, there was no law that said Qing wouldn't always face opponents with similar levels of experience to her.

It was a time when the level of martial studies in Jianghu was unprecedentedly high.

It was thanks to Senior Celestial Martial Emperor who had won the freedom of Wulin from the government.

The now frail, delicate, and sickly Qing protested.

"Still, your disciple actually defeated a Transcendent Master, you know?"

"Is that so? If it was a Transcendent Master, he must have had a title worthy of his prowess, would he not? Tell me."

"Someone called the Demonic Cannibal…"

"…?"

As Ximen Surin was merely humoring Qing when she skeptically asked, she was taken aback when a familiar name was mentioned.

After all, he was a Demonic Adept who was known for his notoriety and had reached a level that surpassed the Mid Stage Transcendent Realm.

"What in the heavens are you saying? The Demonic Cannibal?"

"About that, in a lake called Dongting Lake… Ah, do you know Dongting Lake? It's a super huge lake. In fact, this disciple initially thought it was the sea."

"Is there anyone in this world who does not know of the Dongting Lake?"

\textit{Ah. So she knows Dongting Lake too, huh?}

Qing was a bit sad that she wasn't able to show off her newfound knowledge, not realizing exactly how ignorant she herself was.

"The Demonic Cannibal, you say. Did you finish him off completely?"

"Yes. Just as Master told me, I made him go pop with the Internal Explosive Qi Strike."

"How many times do I have to tell you about your manner of spee… No. Never mind. You did well in that. The bastards called Demonic Humans are known for being narrow-minded and degenerate, worse than pesky flies. It is important to ensure there is no retaliation."

Ximen Surin nodded in satisfaction.

Then, she asked again upon a sudden question coming to mind.

"Halt. Wait. You mentioned the Internal Explosive Qi Strike, but no matter how profound Disciple's Inner Qi is, it would have been impossible to overcome such a difference in levels with just that."

"Ah, about that. Do you know the Buddha's Palm? It's su. per. hel. la. strong. With the Buddha's Palm, your disciple when Bam! Then, the Demonic Cannibal also went Bam! And that's what happened."

Qing made a gesture with her arm as if throwing something, boasting her own supposedly empyrean presence.

As she swung her hand in time with the 'Bam', the cute sound of a bell echoed, going 'Dong Dong'.

"…?"

Ximen Surin was taken aback once again.

Tathagata\footnote{Tathagata is the name Siddharta Gautama\ Buddha to refer to himself}'s Palm. It was an esoteric technique of the Shaolin Temple.

However, it had already become a legend, only recorded in texts.

It was because of a similar martial art called Hundred Steps Divine Fist.

As it was rooted in fist techniques, it matched well with Shaolin's martial arts. Moreover, its power and scope were superior.

Due to this, the direct disciples chose to practice the Hundred Steps Divine Fist, leading to the discontinuation of the Buddha's Palm at some point in time.

It had become Shaolin's lost Supreme Technique.

So, how could it have possibly been unfolded by her disciple's hands?

But to dismiss it as a bluff was impossible, considering the characteristic sound of the bell, a feature only heard from the Supreme Vehicle of Buddhist Qi Arts.

"How… How could this be…"

Ximen Surin was thrown into confusion.

However, since the Inner Qi of the current highest-ranked senior in Wulin was profound, she quickly regained her composure.

"I suppose it is fine. What could possibly be a problem with that? Since those depraved bastards that call themselves Shaolin Monks have neglected their secret technique, what could they possibly say in opposition, even if it continues in the hands of Disciple?"

Ximen Surin's face brightened.

"Serves them right. The esoteric doctrines of those depraved monks, who treated women as if they were some kind of monstrous eccentricity, has ended up being passed onto a woman. Ha! How ironic. The more I think about it, the more gratifying it is. Nothing could be more satisfying. Disciple has truly become a lump of fortune in my later years. Oh my, how can you be so lovely?"

To Ximen Surin, the Shaolin Temple was nothing more than a bunch of fools who outright banned women from entering their sect.

It was as if they thought women would seduce the Shaolin Monks. Ridiculous, considering they were fucking bald.

Upon being faced with yet another fierce oratory from the female activist, Qing didn't exactly know how to respond.

And usually, in such situations, it was best to just smile anyway.

"Hehe…"

"I have told you over and over again to not laugh in such an undignified… Haaa. Never mind. If those depraved monks ever make a fuss about that Divine Art, just mention your teacher's name. Let's see what those fools have to say. Who do those bastards think they are?"

"Yes. Master."

"Very well, there must be a story behind it, but this teacher shall not inquire about the origin of such a Divine Art. Have you perhaps learned any other martial arts?"

Qing gauged Ximen Surin's reaction, trying to decipher whether it was okay to tell her.

{\itshape Seeing how happy she was about the Buddha's Palm, wouldn't it be possible to also tell her about the White Hand Demonic Art without getting in too much trouble?

If she gets a hold of my meridians, it will be exposed anyway.

After all, Master is a guru of traditional medicine!

So, it might be better to be honest now while she's in a good mood, right?}

"Um, well, about that… So, Master. This disciple just happened to have learned a Demonic Art, you see."

"Demonic Art?"

Ximen Surin's eyebrows twitched violently.

Qing hunched her shoulders, shrinking back.

Seeing this, Ximen Surin became weak-hearted once again, softening her demeanor.

"Very well. I understand. It is indeed plausible for a young girl to harbor just one vicious technique when wandering Jianghu alone."

For a martial artist, having an ace in the hole or a Lifesaving Absolute Move was essential.

In that sense, having just one Demonic Art was not that big of a deal.

Ximen Surin thought as such.

"So, what is the name of this Demonic Art?"

Meanwhile, Qing was immensely relieved.

\textit{Oooooh. It's working!}

"Yes! It's the White Hand Demonic Art!"

Qing exclaimed cheerfully.

It was a testament to how much trust she had that her Master would cherish her disciple.

And it was a trust that was immediately betrayed.

THWACK!!!

"EUGHKYAKKK!"

A scream akin to a frog being stepped on burst out from Qing.

It felt like her head had exploded.

Qing grabbed her head and rolled on the ground.

It was a pain that seemed as if her skull had shattered.

In an instant, her face heated up and tears and snot streamed down.

In her consciousness, blanched as white as a blank page, only pure pain existed; it was the very definition of an agony akin to torture.

\textit{HOLY FUCKING SHIT! FUCK! SHIT, THAT'S CRAZY! IT HURTS SO FUCKING MUCH! DID MY HEAD SPLIT IN TWO OR SOMETHING?!}

Normally, a nuclear noogie should have flown her way.

However, Ximen Surin just happened to be holding Qing's gift at the time.

Since times of old and even into the future that would unfold, the flute had been one of the most powerful weapons, as well as worldly possessions, that a teacher could own!

Moreover, the item in question was Fushen-di, a chunk of metal made fully of Ten Thousand Year Cold Iron.

"Oh no! Are you alright!?"

Ximen Surin also startled at her mistake.

She hadn't thought about the Ten Thousand Year Cold Iron Club in her hand.

In essence, she had completely failed to control her strength.

The power was comparable to that of a tungsten rod, which weighed ten thousand eight hundred and thirty kilograms, falling from a dizzyingly high orbit in space\footnote{Strategic Defense Initiative, or in the less flattering term, 'the Star Wars program'}.

Truly a might worthy of being called a Rod from God!

If it weren't for Qing's high Musculoskeletal Stats, a major disaster could have occurred, where a teacher cracked her disciple's noggin.

And in all honesty, even if her skull had been cracked, it would have been considered justified.

To think her disciple was a White Hand Witch!

After all, there was a limit to how much one could tarnish the reputation of both her sect and teacher.

"Stop making such a fuss and get up."

"But, but this really, really hurts……"

A single tear rolled down from Qing's eyes, which had turned red at some point in time.

Ximen Surin sighed deeply.

"Where did you hear about White Hand Demonic- No. Even if you have heard of it, what were you thinking, learning such a heinous Demonic Art?"

"I didn't know Demonic Arts were that bad……."

Qing also had her reasons to feel aggrieved.

It was unknown whether she crossed over timelines, worldlines, or even the computer screen. But the point remained that Qing was a person of the modern era that existed beyond some boundary.

And compared to Zhongyuan, the expressions of the modern world were not just aggressive and radical, but also void of any morals. In essence, there was nothing that was tooheinous to say.

Even if friends casually exchanged insults and curses, no one would despair and declare gravely that it would lead to the collapse of families and society. At best, they would frown.

Moreover, Koreans were known to be more tolerant of harsh expressions than any other nation on Earth.

That was Qing.

There was no shot the significance of expressions like Demonic Arts would register with her.

Had it been named something like Human Trash Arts, Motherfucker Arts, or Life Sentence Arts, she wouldn't have learned it.

So, to Qing, who was a Martial Arts Ignoramus and a gamer at heart, there was no difference between ‘Demonic Arts' and ‘Magic'; they were just siblings of the same Ma family.

To summarize, she didn't think it was all that big of a problem.

"What am I to do with this slow-witted and foolish brat…….."

Ximen Surin had no choice but to let out a frustrated sigh.