\chapter{Ximen Qing (again) (1)}

Do you know the heart of a father on a cold winter day who, despite shivering from the cold, buys a whole fried chicken and carries it home in his hand, breathing out cold air?

Of course, Qing didn't know. She didn't have a child, after all.

But she thought it might feel something like this.

Her steps were light and lively as she climbed up the Divine Maiden Peak with a large bundle on her back, akin to some wandling peddler.

In fact, if one knew the contents of the bundle, they would truly consider her as some mobile peddler.

After all, she had used her remaining gold to sweep up and fill the sack with sweets and ornaments.

Thanks to a wealthy friend, Qing had never used her money. In fact, she rather gathered it. As such, Qing's moneybag was plentiful.

Of course, Qing hadn't been one-sidedly fed because she was a freeloader.

Not that that wasn't the case either, though.

It was because in this era, if Qing took out her moneybag, Peng Daesan and Nan'gong Shencai's reputations would become absolutely fucked.

'How narrow-minded was a man of the Five Noble Clans to mooch off a woman?' That was what people would say.

So, even when Qing would occasionally shout, ‘This meal's on me!', the two would become startled and start begging her to put her money away.

For this reason, Qing's gift bundles could be compared to a certain someone from another world-

A grandfather who only wore red clothes, had a bushy beard, shouted for the equality of all young friends around the world, and distributed items of personal preference for free.

The Divine Maiden Sect disciples guarding the main gate posted Qing and waved their hands frantically.

"Ah, Great Junior Grandmaster! Great Junior Grandmaster is here!"

"Great Junior Grandmaster! Have you returned?"

It was a greeting of pure joy from the girls.

Qing's heart swelled with warmth.

However, she still found the Divine Maiden Sect disciples a bit difficult to interact with.

"Eung. You are all working hard, huh. Here. Take this."

Qing reached into the puddle and, with a neat trick of her hands, fished out sweets wrapped in yellow paper.

She handed out lumps of hardened sugar on bamboo sticks to the disciples, one by one.

"Woah, candied fruits! Thank you so much!"

"Thank you! Great Junior Grandmaster is the best!"

Sweets were a serious matter for women.

Before the start of her journey, Qing was an ordinary production worker who didn't particularly like sweets, but now she understood completely.

There was a kind of ecstasy that only something as sweet as this could provide.

Rinsing one's mouth with tea and then filling it again with sweetness was the very definition of a drug allowed in Zhongyuan.

To be honest, other drugs weren't exactly illegal.

It was because in this uncivilized, primitive, ancient China, laws and regulations regarding the management of drugs weren't properly established yet.

At any rate…

"Thank you so much! Great Junior Grandmaster!"

She watched the bright and cheerful youngest disciples chirping in joy…

"Youngest Junior Master, thank you."

And bowed to the aunty-like Junior Sisters who were actually Sect Elders.

"Junior Grandmaster, hehe… It's sweets…"

And even gave some to the second-generation disciples who were busy rolling around from training.

Qing crossed through the sect, handing out sweets to every disciple she met.

Because of her status and rank, there was no woman to stop her, so her steps were brisk and vigorous.

‘Home Sweet Home' unfolded before Qing's eyes.

The real estate market in Zhongyuan wasn't exactly booming.

But still, how exhilarating it was to have her own home.

It was then.

A girl lying on a wooden bed that Qing herself had made suddenly jumped up and attempted a body slam.

"Sister!"

However, Qing was a Master.

She was long past the point of being caught off guard by such an obvious surprise attack.

"Why are you dodging… How could you…"

"Who are you? This is the residence of Ximen Qing, an Outer Sect Elder. How dare a mere disciple enter without permission? For the sin of not recognizing the hierarchy of this sect, I shall personally give you sweets."

"…?"

Qing swiftly handed a sweet to the girl.

The girl's eyes narrowed.

"What are you even saying."

"Hah? That phrase? Impossible, you… Could it be that… you're Changming?"

"You're so mean."

Honestly, Qing had every right to feel wronged.

The Chen Changming Qing remembered was a kid who was more handsome than pretty.

How could she possibly recognize her at first glance when such a cute little kid turned into a beautiful girl in just half a year?

{\itshape But still… Isn't she the same height as before?

Is the Divine Maiden Sect not feeding her?}

"To think you could completely fool me like this. Your dark scheme is quite impressive, huh?"

"I never tried to fool you, though…"

Regardless of whatever she said, Qing continued to babble and make jokes.

"Iyaaaa, wow! I didn't recognize you because you became so pretty! Our Changming'er is so pretty! So cute! So lovely! So beautiful! Like a flower! Like a Fairy! Hiyaaaa, you're now totally a girl, you hear me! A girl! An actual girl!"

"…? So, I wasn't a girl before…?"

Chen Changming cocked her head, thinking, ‘Isn't this just an insult to me?'.

Then, upon feeling a sudden surge of despondency, Chen Changming's cheeks swelled in frustration.

The tender reunion she had always imagined turned out to be a far cry from this bizarre reality.

"Forget it. I'm leaving."

"Ah. Wait a moment. Look, look! I brought a gift. It's something especially expensive for our Changming'er, so you mustn't blab about it carelessly to others, okay?"

Chen Changming's ears perked up.

"…Especially?"

"Let me see. I'm pretty sure it was here somewhere…"

Qing rummaged through her belongings.

Shortly after, a glittering golden leaf was revealed.

It was a type of hair ornament for women, designed to be secured in the hair by two pronged needles extending from the decoration.

The hairpin, with leaf veins extended into a skeletal shape, had green jade stamens attached to the golden leaf. Despite this, it was not all that big or flashy, but instead quaint and cute.

Chen Changming's eyes widened into saucers.

"Woah…"

"It's pretty, right? Hm, hm. Ahem. I picked it up on the way. You ain't got anything like this at your house, do you? Spring potatoes\footnote{some Korean poem}…Are not what that is."

"What are you even saying."

But despite such words, her face was all smiles.

"Put it on for me."

"Hey. Do you not have hands? Or feet? Do it yourself."

"Hurry up."

I'm pretty sure she isn't at the age to be acting like a baby, though…

Meh, to be fair, Chen Changming was never really in a position to get babied in the first place.

And it continued to be like that even after she entered the sect.

Qing became weak-hearted, thus eventually giving in.

"Sigh. I can't even with you. I'll only let it slide since you're cute."

Since she had been taught exactly where to place the ornament, Qing carefully inserted the hairpin on the right side of her coiffed hair.

-Kukukuku…

"Eh? Oing? Just now…"

"What's wrong?"

Qing tilted her head.

{\itshape Did I hear wrong?

It sounded like a really sly and sinister chuckle……

How strange. I'm pretty sure I heard something, though.}

"It's nothing. I should go see Master now. Wanna come along?"

"No."

Chen Changming's face turned grim.

After all, that was that and this was this.

"Changming'er is so very straightforward, huh? How about at least pretending to think it over?"

"I don't want to."

"Alright. Have it your way then. Meh, she's so assertive."

After unpacking, Qing left her thatch, once again with a bundle of gifts in tow.

Behind her, Chen Changming fiddled with the gold leaf hair piece atop her head with flushed cheeks.

Of course, Qing's eyes were fixed forward.

Hence, she remained unaware that such was the case.

"Masterrrrrrr. Your disciples has arriveddddd."

"Haaa. How dare a fully grown maiden stretch out her words in such an undignified manner? To think this is how my so-called disciple acts. Tsk Tsk."

Ximen Surin clicked her tongue.

Qing's ability to read between the lines translated it as a sign of welcome. She must be happy to see her.

"Hehe…"

"Do not laugh like that. It appears that all my teachings have gone back to Amitabha."

Despite her words, Ximen Surin's face couldn't hide the smile that blossomed.

She nodded after looking in the eyes of her disciple, who had returned safe and sound.

"The glimmer of your eyes look much clearer. It seems you have not out and about, engaging in foolishness somewhere. I feared that the Heavenly Slaughter would worsen. But it seems like my worries were for naught."

It was a complete misunderstanding.

Ximen Surin didn't know that the Heavenly Slaughter accumulated over time was flung away in one fell swoop by Senior Celestial Martial Emperor himself.

She swallowed in relief, thinking her disciple's journey must have been peaceful, simply because the faint signs of Heavenly Slaughter that were present up until her departure were no longer visible.

"Ah. Master. This disciple has brought a gift for you."

"What need is there for gifts? How pointless. Disciple's safe return is more than enough."

"It's a flute. Since you seem to play it occasionally."

Qing pulled out the Fushen-di she had hidden behind her back.

Ximen Surin's expression turned rather subtly complex.

The flute was far too unsightly to call it a gift.

After all, it more resembled a chunk of metal that had not been finished being made into a flute.

"This is…"

"The name of that flute is Fushen-di\footnote{福神笛 'Spirit Blessing Flute'. Bokshinjeok in the original text.}." 

Ximen Surin let out a soft burst of laughter.

"Hoohoo, it seems even Disciple's jokes are humorous at times. You were always calling your sword, Moonlight Sword, after all. Is that perhaps why you have found amusement in naming things? Very well, then. Where did you pick up the name, Fushen-di?"

Qing grinned with ‘that' look again.

The one she wore when she knew absolutely nothing.

Ximen Surin's expression hardened.

"What in the…? Truly…?"

Qing continued to smile brightly.

Ximen Surin took another look at the ugly flute.

Upon closer inspection, it was significantly heavier than its size suggested.

A chill emanated faintly around it and its body, lusterless like the color of the night sea, caught her eye.

Sure enough, it was made of Ten Thousand Year Cold Iron.

And there existed only one flute made of Ten Thousand Year Cold Iron in this world.

"What… Where did you find a Divine Relic such as this? It was supposed to be buried with the Heavenly Queen in her tomb."

Fushen-di was famously known as the beloved treasure of the Heavenly Queen, Xie Naichao \footnote{偰耐超. Seol Neungcho (설능초) in the original text}, who was the Zenith Among Women of her time. 

It also symbolized the marriage vow she shared with her husband, the legendary blacksmith Banchi\footnote{班池. Banchi (반치) in the original text}.

The Heavenly Queen openly declared that, upon her death, this flute alone would be enough when it came to the objects buried with her.

After completing her Wash of the Golden Basin in secret, it was assumed she was buried alongside this treasure.

Such was the renown of this Divine Relic.

For reference, in Zhongyuan, the term, Wash of the Golden Basin, was an excessively elaborate way to describe one's retirement.

Of course, it wasn't excessive for no reason. After all, retirement was actually a significant affair.

The favor and grudges of martial artists were complex.

And of course, it was all the more so when it came to resentment.

So, what would occur if someone suddenly declared, ‘I'm retiring, so let's forget all our grudges~'?

Would their enemies clap their hands, exclaiming, ‘Congrats on retiring!', and proceed to walk away with a thumbs up? Of fucking course not.

They would obviously come rushing with swords drawn, ready to settle scores.

A Wash of the Golden Basin was an official ceremony that resolved even such grudges once and for all.

Naturally, not just anyone could hold such a ceremony.

Only those who had the qualifications could grandly proclaim their intentions for a Wash of the Golden Basin.

Of course, Qing was utterly unaware of such circumstances. As such, she spoke in an ever so bright and innocent manner.

"Ah! Then that must have been the Heavenly Queen's burial chambers."

Ximen Surin's expression grew serious.

What exactly had her disciple been doing over the span of her Jianghu outing?