\chapter{Ximen Qing (again) (5)}

It seemed that the warm spring sun had come only during the day.

Then, in the blink of an eye, the weather became completely mild.

How swiftly time flows.

Suddenly, flowers blossomed and the day was sunny—spring was in full bloom.

Qing had been walking around naked since the beginning of winter, enduring the chilly early spring weather for over four months.

In Qing's residence, windows and doors had been refitted and her bedding had been rearranged.

The missing clothes and undergarments had returned as well.

\textit{But this outfit is just so comfortable…}

A garment made of very thin, semi-transparent fabric joined in a cylindrical shape with two straps over the shoulders.

It was light, flapping around weightlessly.

And the length, reaching to the thighs, was convenient and unobtrusive in movement.

It was the birth of her favorite pajamas.

Wearing comfortable pajamas and getting into bed felt like paradise. Nothing could be better.

Above all, not wearing underwear was a whole new world.

At first, it was so embarrassing she wanted to just die in some hole.

But once accustomed, it felt like there could be no greater liberation in the world.

The very definition of freedom itself!

It was because the primitive weaving technology of ancient China had not invented stretchable fabrics.

As a result, there was a certain inconvenience of having to tie knots with strings.

And for Qing, it had always been a great ordeal.

Due to this, for a while, every single day was a nuclear noogie fest.

\textit{Shit, fucking hell, how can she just notice I'm not wearing underwear right away?}

\textit{Does one gain x-ray vision upon becoming a Master?}

\textit{Like hello? You wouldn't let me wear it when it was cold as fuck.}

\textit{But now that it's a bit warmer, you beat the shit out of me for not wearing it…}

Qing's lips protruded sulkily.

Ximen Surin sighed deeply at that sight.

"Should I have just made her roam around stark naked…"

"There wouldn't have been much difference even if you, agh."

Right as Qing cheekily retorted, she received a nuclear noogie.

However, the magnitude of Qing's screams had significantly decreased.

It was thanks to the Protective Mirror Qing had honed over the winter.

Now, a nuclear noogie was nothing to fe-

Thwack!

"KUAGH!"

Qing rolled on the floor.

Humans were creatures that continuously evolved!

Moreover, the person in question was Ximen Surin, a woman who had defeated numerous formidable male Masters and stood as one of Wulin's Ten Masters Under Heaven.

Adjusting the power of a nuclear noogie was simple for Ximen Surin, whose very life was a constant struggle.

In the first place, no matter how impressive a Protective Mirror in the Late Stage Peak Realm was, it was nothing before a fist of the Profound Realm.

"How is Disciple getting so increasingly careless and irresponsible?"

"Kkeugh. Sob. It really hurts…"

"Indubitably. After all, I hit you so that you would feel pain. What else did you expect? For it to tickle? I cannot understand how you are acting more childishly as you get older."

"Hehe…"

Qing chuckled in embarrassment.

Ximen Surin just completely turned her head away.

How could she not be aware that her disciple was acting spoiled because she felt an increasing fondness for her teacher?

As such, Ximen Surin was also cautious about constantly giving in to her disciple.

Still, it could be considered an improvement. When they first met, Qing behaved utterly like a man.

But now, although still rough like a male farmhand, she seemed like an actual girl.

"So, you are planning to leave soon? Where do you plan to visit this time?"

"Mm. I'm not sure. Wherever my feet take me, I guess?"

"If that is the case, stop by the Emei Sect."

"O-Oh uh. The Army Sect?"

Qing barely contained her patented ‘Oooh'.

\textit{But anyway, the Army Sect? The name was quite extraordinary.}

\textit{It seemed like a place with hella fangirls\footnote{BTS fans call themselves Army}.}

"That is right. This teacher has a deep friendship with the Chief Abbot of the Emei Sect, so while you are there, go inquire about her well-being and learn some of their basic cultivation techniques."

"Uh, will they really teach me just like that?"

"Of course. If it is Dingtie Yuan-ni \footnote{丁鐵 緣尼 Jeongcheol Yeonni (정철연니) in the original text}, she will gladly pass on the techniques, so there is no need for Disciple to worry."

"But, is the Emei Sect far away?"

"It is not too far, though the journey is not easy. It is located west, in the land of Sichuan."

"Sichuan!"

Qing exclaimed.

Sichuan was the most familiar region name to modern Koreans.

There were many things associated with Sichuan, after all.

Sichuan Jjajang, Sichuan sweet and sour pork, Sichuan Jjambbong, and even mala hotpot!

Truly a land for gourmets where chili oil flowed instead of water! (Not actually.)

Even before the start of her Wulin journey, Qing had enjoyed spicy food.

During her poverty days, she was too desperate to survive, so she couldn't even think of visiting. And then, once she became a master she had forgotten all about it.

"However, you need not reach the Absolute Sword Wall until you have reached the Transcendent Realm. Even if Disciple, at your pathetic level, were to acquire the profound Insights left by the Celestial Emperor, would it not be mere pearls before swine?"

"Master?"

\textit{What the? Aren't I getting shat on again?}

\textit{Could it be that even Master…?}

"Haa. Moreover. It seems Disciple has some sort of connection or fate with peerless martial arts. But that does not mean you should learn just any martial arts. And especially avoid cultivating further in the Demonic Arts. Do not even think of doing such a thing."

"Aiyaaaa. I won't do that anymore."

Ximen Surin's eyes narrowed.

"How am I supposed to believe you when you are this untrustworthy?"

"Now I know better, okay? And well, I mean, who in the world would ever threaten me with a sword and force me to learn Demonic Arts? Unless that happens, I would never."

Thwack! Qing rolled on the floor again.

"The words that come out of Disciple's mouth are becoming increasingly ridiculous. Your manner of speech is one thing, but carelessly uttering such words should never be done. Words have power and unnecessary speech, behavior, and actions will eventually return as karma."

Qing rubbed her head as she thought.

\textit{Karma? The fuck? At least say something that makes sense…}

\textit{Who the fuck would ever go as far as to threaten someone with a sword to learn Demonic Arts…….}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Such a direct visit is an honor of a thousand lifetimes."

"Enough. What about that bitch? Is she still in the Divine Maiden Sect?"

"That is correct."

"Aren't those wenches of the Divine Maiden Sect bitches that just hole up there together, only mingling among themselves? Couldn't it be that she is just not coming down? Can't we just storm in and take her?'

"The known realm of the Godmother is the Profound Realm. If she has advanced further, the damage to the Divine Cult could be…"

"Tch. Are you saying I have to put up with an old wench out of fear? Me?"

"My apologies."

"Then, let us wait until summer. Have you spread the kids out over there? Will they contact us right away?"

"Yes, they will."

"What if that bitch doesn't have Fushen-di?"

"Fushen-di is an invaluable treasure. When it comes to such a treasure, even parents and children are rendered meaningless."

"Then, what if Fushen-di has already been blown? We cannot wait for another forty years. Will the Orthodox Faction bitch cooperate easily?"

"We just need to force her to learn Demonic Arts. Once she becomes a public enemy with nowhere to run, she will have no choice but to join the Divine Cult."

"Those Orthodox Faction fuckers. Narrow-minded idiots. Very well, then. This is why I like our Secret Pavilion Leader so very much."

"It is an honor of my three lives. All shall worship. Glory to the Heavenly Demon. The Divine Cult shall reign all under the heavens."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{Agh shit, I think I tied this way too tightly.}

Even if one was accustomed to something, if not done for a long time, one tended to lose the knack of going about it.

Qing awkwardly grabbed the fabric around her buttocks and pulled.

\textit{How strange. It keeps sticking into the crack.}

\textit{Did I gain some weight?}

Having roughly packed everything, it was now time to head back into Jianghu.

Contrary to before, leaving her beloved home did not actually evoke a sense of regret.

After all, this time, she had suffered far more at home than outside.

No matter how many times she thought about it, making her endure the winter with just one set of pajamas seemed way too harsh.

Because of such thoughts, her steps were light when leaving.

And as she did so, Chen Changming blocked her spirited steps.

"Sister, you're leaving again?"

"Of course. I gotta go."

"Can't you just not go."

"Nope, I can't."

Qing had much to do.

First, to reach the Transcendent Realm.

Then the Unrestrained Realm, Profound Realm, and so on and so forth.

Ultimately, she had to settle scores with Lil Window.

After all, she couldn't keep living in this state. The anxiety was fucking killing her.

"Rea-"

"Don't do that ‘Really Really' stuff. It's not cute, alright?"

"Tch."

"Aren't you way too easy to read? It's so obvious that it's boring."

"What are you even saying."

Though she said this, Chen Changming's voice lacked any semblance of strength or bite.

Watching her gaze slowly turn to the ground, Qing spoke in a gentle voice.

"Can't you at least reach the Peak Realm? It needs to be that much for me to ask Master if we can take a trip around Jianghu together, you know?"

Chen Changming's head snapped up.

"Would the Peak Realm be enough?"

"Well, who knows. It depends on Master. But wouldn't she somehow allow it if I ask nicely? Though it probably can't be too far, somewhere close should at least be fine."

Qing thought it might be possible, given Ximen Surin's personality.

Though other disciples might not think so.

"Then, have a good trip. I'm gonna go."

"What? Go where?"

"To train."

Her enthusiasm was at its absolute max.

Qing chuckled and waved her hand.

After parting with Chen Changming, Qing set out on her journey again.

The Divine Maiden Sect disciples she encountered sent her off with smiling faces.

"Great Junior Grandmaster! Bring something tasty!"

"Great Junior Grandmaster! My hair feels a bit empty. It'd be nice to stick something pretty like a hairpinnnn."

"Junior Grandmaster, eat this when you get hungry."

Right as she was going through this…

One of the Divine Maiden Sect disciples handed her a pouch.

"Great Junior Grandmaster... here."

"Eh? Huhhhh? This is for me?"

"Please take care and return safely."

When she took a peek, she saw that it was a modesty panel woven from red silk.

\textit{I'm thankful and all, but I hope it fits…}

\textit{Since I'll get sweaty if it's too tight.}

"Thanks. I'll make good use o……."

Before Qing could finish her thanks, the Divine Maiden Sect disciple had run away with her face covered.

\textit{Eh? Why you running away?}

Qing was unaware.

Over the winter, she had become an ideal type known as the Reincarnated Divine Maiden to many of the Divine Maiden Sect disciples.

It was because Qing's… stage costume had been that impactful.

Of course, the performance itself was also extraordinary.

And Divine Maiden Sect disciples who were fans of such a scene had given heartfelt farewells.

"Junior Master, when you return, let's go shopping for supplies together, alright? It's a promise, okay?"

"Please…Come back. No matter what."

"Great Junior Grandmaster, I secretly buried a bottle of liquor last time. Let's drink it together when you return, okay?"

"Junior Grandmaster, when you return this time, I have something important to tell you. It is really, really important."

\textit{But… why?}

\textit{Why do they all sound like raised flags?}

\textit{Aren't they making me seem like I might not return or something?}

Nevertheless, Qing was one who strived to live simply. She didn't put much thought into anything that seemed too complex for her..

As such, receiving such warm farewells lifted her spirits once again.

Qing hummed a tune as she passed through the gate and descended the slopes of Divine Maiden Peak.

As her mood was greatly uplifted, she had a very good feeling about this outing.

Like… Somehow, it felt like this journey through Jianghu would be filled with ease and good events.

Or at least, that was how it was until about an hour later, when she was kidnapped.
