\chapter{Ximen Qing (again) (4)}

There was a rather touching narrative here that could not possibly be heard without a few tears being shed.

Previously…

As Ximen Surin returned Fushen-di, she said…

"This teacher is already old, so there is no need for a new flute when I have an old friend, worn with my use."

Upon hearing this Qing began to yap.

"Master, this is basically a designer good worth ten thousand gold, you know? It's one of the best treasures under the heavens! But right now, it's free! An exclusive benefit just for Master! Brought to you by this disciple's fervent heart!"

Ximen Surin was about to punish her with a nuclear noogie but hesitated.

Fushen-di was indeed a priceless treasure, which could not be bought even if there was a blank check.

Yet, if one just had to put a price on the treasure, it would be around ten thousand gold.

For reference, something worth less than ten thousand gold would not befit the stature of a treasure.

And if one possessed at least ten thousand gold, their family would not need to work for multiple generations; they were able to live solely off of such money.

Thus, ten or twenty thousand gold made no real difference. It was a huge amount regardless.

The reason why Ximen Surin was surprised was because Qing, unexpectedly, knew the exact value of Fushen-di.

She thought it was just given out of her disciple's ignorance regarding its value.

But to think she unhesitatingly offered it to her teacher while knowing its worth…

It was enough to make the heart of an elderly woman ripple with waves of emotion. In short, she was deeply touched.

\textit{Yes. As I thought, this child is truly kind.}

\textit{She is a little one, born with Heavenly Slaughter, yet still so upright.}

\textit{Though she is a bit obtuse…}

\textit{No. But still, there should be a limit to how dumb she could be. Isn't that so?}

\textit{Even utterly plain water would not be this dull, would it?}

However, gratitude was still gratitude. It was not an emotion that could be controlled.

She could not help but feel that her disciple's heart was truly commendable, joyful, and lovable.

Ximen Surin smiled warmly.

"I shall just receive your thoughtful heart, then. You may keep it for yourself."

"But I don't even know how to play it."

"Shouldn't a woman at least be proficient in one of the Four Arts?"

The Four Arts referred to Qin (music), Go, calligraphy, and painting.

They were the most esteemed hobbies acknowledged in Zhongyuan.

After all, it wasn't just a simple hobby.

It was akin to yachting, horse riding, golf, and clay shooting in modern terms.

Basically, engaging in them made one appear very sophisticated and refined.

In Zhongyuan, the Four Arts had such an effect.

"Opportunely, there is a fine flute available and music soothes the human heart, thus serving as a tool to quell restlessness. It will also greatly help in calming Disciple's murderous internet. Your Killing Star."

Thus, playing the flute was added as her minor along with her major which was training.

Therefore, throughout the winter, she played the flute incessantly, despite the freezing cold.

Naturally, the melody was utterly upsetting and a rather desolate emotion was aroused in spite of herself, leading to tears flowing freely.

But then… One day? She was able to actually play a note. And the more surprising part? Henceforth, she began to play it rather well.

No, it was an insult to merely call it at a level of ‘playing well'.

To Ximen Surin, it seemed as if melodies unheard of in the world freely burst forth.

The unexpected achievement of her instrumental prowess was enough to evoke immediate admiration.

"You are truly one that could establish an entire school of music. No, strike that. You are a talent that deserves to write an entire history! I had no idea that Disciple had such a gift!"

When hearing that, Qing was about to smile shyly.

But then, she thought perhaps Ximen Surin might offer a blanket if she saw her shivering so severely from the cold. So, Qing gazed at her master ever so pitifully, hoping it might rouse her sympathy.

There was no such return, though.

Of course, the nature of that supposed talent was plagiarism.

Any person from the modern era would have certain melodies they remembered.

And unless it was an extremely radical category or genre, to the ears of those in Zhongyuan, it would seem like a shocking breakthrough. One that leaped to a new era, beyond even the most fundamental forms of music.

Among them, the Divine Maiden Sect disciples considered two melodies the finest of them all.

Canon in D and Merry-Go-Round of Life.

Of course, it was incomprehensible why such an optimistic hymn was named after a brutal ‘cannon'.

Nor could one understand what a merry-go-round and a nostalgic melody evoking past beauties had to do with each other.

But what did it matter? The music was good.

For Qing, it was a relic of the past that existed before the start of her Wulin journey, evoking a certain nostalgia for her homeland.

Her previous life wasn't all that excellent, but she had still lived alone in content.

Such a time was clearly better than her current cold and embarrassing state.

So, the tunes she played on the flute could only be memories that did not exist in this world.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Wulin Alliance headquarters was in turmoil.

It was due to a newly confirmed report.

The issue started with a protest from the Fort of Yangtze River Waterway.

A lone enforcer of the Wulin Alliance was apparently part of a covert group known as the Association and was also a wicked sorcerer who controlled Blood Jiangshis and Living Jiangshis.

Moreover, the son of the Waterway Forts Commander had even lost his life because of her.

The Wulin Alliance immediately sent martial artists to the Yun Clan of the Jin Prefecture to verify such testimony.

And all that resulted from it was a return from an already decrepit estate of the Yun Clan.

Without a child constantly sweeping and cleaning in wait for someone, like Qing's thatch had done, even a large house would quickly fall into desolation.

Thus, when the investigation team stormed into the Yun Clan estate, they found nothing but ruins with no signs of any recent human presence.

What was surprising was the testimony of the city residents.

After all, they claimed they had seen many members entering and exiting the Yun Clan estate up to just seven days prior.

This supported the statement from the Fort of Yangtze River Waterway that Yun Yuanling had wiped out her own clan and turned them all into Jiangshi.

In essence, no one was living in the Yun Clan of the Jin Prefecture in the first place.

As such, this meant that there existed a force that included the Demonic Cannibal and the most powerful Jiangshi Sorcerer of Zhongyuan; an organization cunning enough to operate right under the nose of the Wulin Alliance.

The Wulin Alliance had to prepare a response to this danger.

And so, this great gathering of the Orthodox Faction was about to mobilize its heavy and enormous body in an effort to confront this mysterious and dangerous Association.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

To be frank, when Ximen Surin told Qing to undress, it was not actually for training but rather for punishment.

She was a despicable, disgraceful disciple who lacked any alertness and awareness, was foolish, and even learned Demonic Arts without a single care. A figure who endangered both her teacher and sect.

Thus, this was the most severe punishment she could think of giving her.

\textit{But, what's this?}

Normally, tears should have been trickling down as she pleaded for anything but that punishment.

In fact, it was a punishment that evoked even more shame because she had to display such an appearance to her juniors.

Ximen Surin would have rather bitten off her tongue than do such a thing.

If not, she might have even broken her own dantian and severed the muscles and tendons of her own limbs, complaining she would rather maim herself than deal with such fuckery.

\textit{But…? What's with the state of Disciple?}

\textit{Oh my heavens! How could she be so shameless!}

Yes, she was a bit embarrassed, but that was all there was to it.

In reality, the cold was a far greater concern to her than shame.

As such, this was the greatest crisis Ximen Surin felt among all the various incidents she had witnessed from her disciple.

After all, a woman should know the shame that inherently comes with her gender.

One must know that there were things more precious than life itself.

So, she had seized all underwear and bedding, even stripping the windows and doors from the thatch.

It was to make her disciple realize how hideous she looked and how ashamed she should feel from it.

However, she merely shivered without feeling any embarrassment.

Baffled and incredulous, she left her be.

And when she secretly checked at night, fearing she might actually freeze to death…

\textit{What in the heavens was this!}

Her Protective Mirror rose automatically to safeguard her body!

Protective Mirror was a type of art that shielded the body with Inner Qi.

Every night, Qing subconsciously surrounded herself with Protective Mirror to survive.

And when using Protective Mirror, the highest skill was considered to be such an unconscious operation.

After all, couldn't it only be called a Protective Mirror if it sprung forth in times of danger, even without conscious thought?!

Yet, in reality, even Masters who reached the Transcendent Realm and used Reinforced Qi Armor in major confrontations had to exert effort to raise their True Qi consciously.

If one could use Protective Mirror as naturally as breathing…

They would have to be in the Mid Stage Unrestrained Realm. That was the only way such a thing could be attained.

Ximen Surin reconsidered her way of thinking.

Yes, her disciple was one who didn't know shame.

But if, by chance, this all too natural and instinctive mastery of the Protective Mirror could be achieved….

Then, at the very least, she wouldn't lose her life when she ventured back into Jianghu. After all, it was akin to constantly wearing powerful body armor.

Indeed, there were things more precious than life.

But still, Ximen Surin desired beyond all else for her disciple to continue to live and breathe.

Thus, she had no right to criticize Yang Xiaoyue, that terribly runaway disciple, who burdened her own child with such karma.

The heart of a mother who merely wanted her child to live, even if it meant bearing scars for the rest of her life, must have felt like something like this.

If only Qing could remain forever ignorant, thinking of it only as memories where she had to suffer a bit.

\textit{I am sorry for this extreme selfishness. I am sorry for being such a bad teacher.}

But, it couldn't be passed as mere suffering.

It was abuse.

After all, what kind of teacher allowed their disciple to endure such a state?

There was nothing she could say, even if Qing resented her and considered her an enemy later on.

But even if her own disciple were to turn against her, sword drawn, Ximen Surin could not let go of this opportunity.

After all, her disciple had to return to Jianghu eventually.

If the public knew, she would surely be criticized for her decision.

Even so, Ximen Surin decided to bear it all.

Of course, if Qing knew such sentiments, she would say it was an unnecessary worry.

'Couldn't I just be cold at night? Why do I have to be undressed for the entire day? It doesn't really have to be abuse, right?' She might pout and grumble as such, feeling chagrined.

Nevertheless, it was a significant resolve for Ximen Surin.

-For that reason…

The Divine Maiden Sect disciples benefited.

Unlike Qing, who was chilled to her very bones, the winter at the Divine Maiden Sect was exceptionally hot.

It might as well have been called the Volcano Peak instead of the Divine Maiden Peak.

Why, you ask? Of course, it was because the youngest adult of the highest rank in the sect wore such indecent and vulgar clothes.

It was questionable whether the thin fabric should even be considered clothing. After all, it clumsily revealed the body's contours and was practically see-through.

There was no exaggeration in this. Indeed, even a femme fatale known for her allure in Jianghu wouldn't wear such provocative attire.

However, unbecoming of such ‘hot' attire, Qing was completely pale, shivering intensely.

Her appearance was utterly pitiful.

And as her pitiful state hid her seductiveness, it actually bloomed her into an undeniable belle.

Of course, it was true that playing the flute stimulated her Inner Qi, which then subsided the cold.

But still, when she started gracefully playing the flute, as if she hadn't been pathetically shivering before…

A beauty descended upon these plains. One who played such beautiful melodies with tearful eyes, steeped in intense longing.

Originally, the charm of music was in creating an atmosphere that had never existed in the world before.

And fitting of that, the uniquely atrocious outfit instead brought forth an emotion that could never have been anticipated in this world.

How elegantly lewd! How calmly provocative!

The very definition of a moving collection of erotic paintings!

No, forget eloquence! It was just lewd! No matter which way one viewed it, it was way too provocative!

The complete incarnation of Mara-Papiyas!

Mara-Papiyas, also known as just Mara, was the supreme evil deity in Buddhism.

Surprisingly enough, there was always a common thread in the mythologies of the world, so it could be said that he had a similar role to Lucifer as described in the Bible.

Mara governed desire and was a symbol or the very embodiment of passion.

The character ‘Ma' in ‘Mara' was the same used when referring to ‘Magong', also known as Demonic Arts.

He was most famously known for the incident where Mara was rebuffed while trying to tempt the meditating Buddha.

At any rate, whether elegant or calm, the conclusion remained the same.

The mere sight of Qing would cause one's body to inevitably heat up, causing warmth to rise from behind the dantian.

So, in this cold time…

Oddly enough, there were a great many disciples plastering their bodies against one another and interlocking fingers with each other.

Moreover, even the strict hierarchical barriers of rank and status were breached, with several disciples and masters sharing a bed.

That was the kind of winter that went warm.