\chapter{Ximen Qing (again) (3)}

Qing vigorously rubbed her head.

To be honest, massaging a wound didn't necessarily make it any better.

But what else could she do? It hurt so fucking much.

\textit{Ah shit, it still hurts like a bitch……..}

\textit{Isn't it possible that my scalp got torn?}

As Qing rubbed vigorously, she intermittently checked her hand.

She was making sure if there was any blood that had rubbed off.

But surprisingly, her hand was clean.

Heh? But it feels like something got torn, though? That's weird.

Qing was originally prone to overreacting.

But this time, it seemed she was truly in pain.

Seeing her in such a state, Ximen Surin felt a surge of pity.

Just as there were no parents who could win against their children, a proper teacher could not best their disciple.

"Haaa. Fine. I see. Even though you have learned the Demonic Arts, I see no malice in your eyes. It is clear that Disciple is being careful. I understand."

It was a ridiculous misunderstanding, but nevertheless, she meant that she would let go of her anger.

Qing responded with a bright expression.

"That's right. As long as I don't get caught, iz all gud-"

Thwack!!

"AHHH! T-The place where I got hit… Again. Euhhhhh…"

Qing unnecessarily inserted slang and ended up receiving another nuclear noogie.

A single teardrop once again rolled down…….

Ximen Surin shook her head.

"Indeed, as long as you are careful… As long as you are careful…"

Ximen Surin trailed off.

But still, no matter how careful she is, isn't that Demonic Art far too wicked?

No wonder her hand looked so unusually beautiful.

"White Hand Demonic Art directly cuts through flesh and bone, thus accumulating malice. A person becomes increasingly evil and eventually turns into a monster that finds joy in murder itself. Disciple must remember this and use it only in truly dire circumstances."

To be fair, by that standard, it was already far too late for Qing.

The monster specializing in killing evildoers, clad in human skin, promptly replied.

"Yes! Master."

"Alright. Since you have already learned it, there is nothing we can do anyway."

It wasn't like she could destroy her disciple's dantian and sever her muscles and tendons to cut off the very roots of the Demonic Art.

Of course, though, those who called themselves the Orthodox Faction would surely attempt to do so if they knew about this.

After having such thoughts, Ximen Surin felt a simmering irritation once again.

\textit{What is so wrong with this foolish brat learning some Demonic Arts?}

\textit{Despite the divine punishment of Heavenly Slaughter, she grew up so well. She is such a kind child. What sin has she made to deserve such cruel reception?}

These were the thoughts of Ximen Surin, who had, in fact, killed countless Demonic Humans in the past.

"Very well. Disciple, if ever you are caught using that Demonic Art, there is something you must remember."

"What is it?"

"Kick up a fuss and deny it to your last breath."

"Excuse me?"

Ximen Surin spoke gravely again.

"Just claim it is not a Demonic Art. Hm. Just say… Yes, you can just say that it is a Divine Hand Arts of the Divine Maiden. Something like that should suffice."

She was telling her to stubbornly lie, thus denying the truth.

Qing thought.

\textit{So, I guess the biggest yappers win in Jianghu too, huh? Loud makes right?}

"Uh… Is that fine? Can I really do that?"

"Of course not. At least, not usually. If they persist, say it is a martial art that this teacher of yours created. What can they possibly do then? How could those mere things dare to challenge that?"

Qing was unaware of this, but it was basically a vow from a renowned martial artist that she would put all her honor on the line to share the burden with her disciple.

"Won't we get caught lying, though?"

Ximen Surin smiled broadly.

"That is why you must practice from now on."

"Practice?"

"That is right, my disciple. Your Inner Qi is of a righteous, orthodox nature, which does not suit the extremely evil White Hand Demonic Art."

Ximen Surin imparted her teachings.

Yin and Yang were fundamentally classified into four types.

The energy of the sun was Yang.

When hot, it was Pure Yang, and when bright and righteous, it was Orthodox Yang.

The energy of the moon was Yin.

When dark and evil, it was Unorthodox Yin, and when cold, it was Pure Yin.

When inserting the Golden Mean into these four types, it became eight.

The reason for that was because the Golden Mean was not considered a quality in itself, thus making it eight.

It was simply hot. It was hot and bright. It was clear and virtuous.

It was hot yet evil. Golden Mean. It was bright yet cold.

It was dark and evil. It was cold and dark. It was simply cold.

Pure Yang, Extreme Yang, Orthodox Yang.

Unorthodox Yang, Golden Mean, Orthodox Yin.

Unorthodox Yin, Extreme Yin, Pure Yin.

This arrangement colored the energies of Yin as blue and Yang as red in the diagram known as Tai Chi Yin and Yang.

When adding the attributes of Fire, Wood, Water, Metal, and Earth to this, it became the Yin, Yang, and Five Elements, a principle encompassing all things in the universe.

Previously, when Ximen Surin grasped her meridians and pulse, she had found that the Yue Maiden Cultivation Technique that Qing had learned was based on the Dao of the Golden Mean.

And the Zhu Xiang's Heart Cleanse Mirror, created with the Imagery of Yan Emperor Shennong, was a breathing technique that contained the energy of righteousness among the Yang qualities: Orthodox Yang.

Late Blooming Heavenly Love Cultivation Technique, a subcategory of Fairy Arts, was also the same.

This meant that Qing's current Inner Qi was biased towards Orthodox Yang.

The sunset yellow glow of Qing's Sword Qi was proof of this.

"White Hand Demonic Art is a martial art based on Unorthodox Yin. So, if Disciple handles it with righteous energy, won't the traces differ from those of Demonic Arts?"

If one could separate and handle only the energy of Orthodox Yang from their flowing Inner Qi, the traces of use would diverge, even if it was the White Hand Demonic Art.

Then, they could obstinately insist it was something else.

And strictly speaking, it would be a lie either.

"So, how do I train something like that?"

"Fortunately, is it not the season of winter now? My disciple, it appears fortune has followed you, thus allowing you to seize this opportune time. Yin and Yang become stronger when colliding. As such, it is natural for Yang Qi to surge when the External Qi is Yin."

"So, you're saying it's good to train in the winter?"

"Indeed. As such, it is not that difficult a training. In fact, it is rather simple. Very much so."

\textit{Simple training!}

Qing's face brightened.

"Then, what does this disciple need to do?"

Ximen Surin replied.

"Undress."

"Excuse me?"

\textit{Hehhh? Oing? Eh? Did I hear that wrong?}

\textit{I think I heard something weird, though…}

Qing hesitated.

Upon seeing this, Ximen Surin spoke again.

"Only in the cold does warmth truly come to you. Isn't that the case?"

"Uh, so what that means is……."

Ximen Surin smiled benevolently.

"That is right. All you must do is feel the Yin Qi of the world directly on your bare skin. How could there be a training simpler than this?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

To people, a house was not just a place to stay.

A house held a value far beyond that.

This value could be expressed in a single phrase.

A comfortable and warm refuge.

Thus, a house that was neither warm nor comfortable was no longer a house.

It was merely a space that uncomfortably confined someone, suffocating them with anxiety.

In that sense, Qing had lost her home.

"It's so cold…"

Qing shivered as she thought.

\textit{I finally managed to get my own home after going through so much!}

\textit{But now, I can't even light a fire in my own house!}

\textit{And she took all the blankets away!}

\textit{She even removed the windows and doors!}

And then, all that was given to her for clothing was a single, extremely thin piece of fabric with shoulder straps.

Originally, the purpose of clothing was to protect the body, so this piece of fabric could hardly be considered garment.

Even her underwear was taken. Every single fucking one of them.

The winter wind at the top of the Divine Maiden Peak was fierce.

It didn't stop at just chilling the flesh; it was as if it dug into her skin, permeating deep inside.

The winter wind blew up and down, burrowing in without resistance. But it didn't even need to be so fierce. After all, the thin piece of fabric was so well-ventilated that the icy wind moved through it akin to leaving a door open.

\textit{I'll tell you everything I know… From the location of my base to how to decode all our codes.}

\textit{Please, just give me one blanket…}

\textit{No, wait. On second thought, this pisses me off.}

\textit{This bullshit is supposed to be training?}

\textit{Shouldn't I just run away now? Better late than never, right?}

Despite Qing's anger, the results could not be denied. Rather, they were outstanding.

After all, she was still alive and breathing.

No matter how strong a Master was against the cold, there was still a limit.

Surviving a harsh winter wrapped in just a thin piece of fabric was impossible.

Initially, when she thought she was going to die, a surge of heat wrapped around her body.

After warming her just enough to prevent death, the spiteful heat subsided.

And then, after a month and a half of that…

Now, she could skillfully handle the True Qi of Orthodox Yang.

It wasn't that she wasn't cold.

It was just that she could maintain the minimum body temperature.

For this reason, Qing had become the very personified concept of shivering.

In fact, if asked what an earthquake was, someone could just point at Ximen Qing for a dynamic, visual understanding.

Chen Changming, who had come to bring her food, watched her in such a state.

"Are you cold?"

"I-I t-think I-I'm a-actually gonna d-die……."

"Then, Sister, do you want me to hug you?"

"Uh……"

Qing was conflicted.

However, the laws of her proud nation were strict and the heavens and earth were clearly gazing upon her. Isn't that right?

It wasn't even an emergency situation or crisis like before.

How could she dare hold a minor in her arms?

Of course, child rights were not established in Zhongyuan.

Laws protecting Children and Juveniles from Sexual Abuse existed only in Qing's mind.

"N-N-No…….."

"Tch."

"B-But c-could i-it be that t-today's l-lunch t-too is……"

Jin Jangmyeon opened the lunchbox she brought.

"Cold Buckwheat Noodles. Cold Salad."

"Ah. P-P-Please…….."

In the end, Qing couldn't help but let a teardrop trickle down.

In primitive, uncivilized, ancient China, Cold Buckwheat Noodles was simply a term for noodles in cold broth.

That, along with cold vegetables and various meats that had been boiled and cooled, made up a three-layered lunchbox.

\textit{Please, something warm. I just want to eat something warm.}

But even in this cold, she was still hungry. That couldn't be helped.

Qing scooped up the Cold Salad as she thought.

\textit{Ah. But it really is delicious…}

Despite her grumbling, Qing completely cleaned out the lunchbox, before curling up in a corner of the room and hugging her knees.

As there were neither windows nor doors, a storm raged inside the house.

The corner she found was a relatively less windy spot.

But still, if she got too close to the wall, the cold would burrow deep into her bones.

As such, it was a spot that was subtly distanced from the wall.

"Play the flute for me."

"H-H-How c-can I-I-I-I p-p-play, oh my god."

Qing couldn't control her shivering, her whole body vibrating as if she was having a seizure.

Still, shivering this intensely once helped her feel a little better momentarily.

"Play the flute for me."

"Ah shit. That's cold, though. It's not a flute. It's like a block of ice. My fingers will freeze."

"Sister, hurry up."

"Why is a tiny little thing like you so persistent…"

\textit{Sigh.}

Qing picked up Fushen-di (value estimated to be around ten thousand gold) that had been flung away in a corner.

It was a flute made entirely of Cold Iron.

There was no way blowing into it normally would produce a sound; she needed to utilize the subtlety of Sound Transmission and breathe into it with her Inner Qi infused.

Ximen Surin had explained it to her.

Once it produced a proper sound, the owner's Inner Qi would remain within it for decades, preventing all others from playing it.

However, it was too cold, so she only listened to half of the explanation, and the other half was too complicated to understand anyway.

\textit{I guess I just need to blow into the lockscreen?}
