\chapter{Hidden Dragon Martial Arts Tournament (5)}

"Hm. So who do you think will win?"

"Young Expert Wang has a good amount of experience in real combat, but
can he really be compared to the legitimate disciples of the Nine Great
Sects? Furthermore, his opponent is Brother Bung Sain of the Kunlun
Sect."

Bung Sain was a Kunlun Sect disciple with a title of Jade Dew Sword.

He had a sensitive personality, so he was given that moniker because he
would cry whenever he was happy, sad, or even just seeing someone
else sad.

"Is that so? Hey, what are the odds?"

"Young Expert Wang is at seventy-eight percent and nine points. Daoist
Bung Sain is at one percent and one point."

"Hm. In that case, I'll bet one nyang on Young Expert Wang."

Qing purchased a stake on Young Expert Wang's victory.

At this, Jegal Ihyeon interjected.

"Sister, why bother wasting a whole silver nyang on a stake for a
martial artist who will clearly lose?"

"Isn't this all for fun anyway? If I bet on Daoist Bung Sain, I would barely
make about ten mun with just a copper coin, but if Young Expert Wang
wins by some miracle, I'll get a little less than seven nyangs."

"Isn't that exactly the kind of thinking that leads to ruin?"

"Well, it's not like I'm betting a lot of money……"

And so, the non-combative sparring began.

Unexpectedly, the martial arts that used a chair looked quite great.

It wasn't a typical square chair, but one that was horizontally long and
used in old taverns by two people.

The edges of the seat were reinforced with steel plates and the legs of
the chair were sparsely wrapped with steel wire.

The sight of the special chair being wielded this way and that was truly
the epitome of both offense and defense. While blocking the attacks,
he would also thrust with the chair leg, hook and pull with the wire
wraps, or strike with the steel-plated edges, thus exhibiting his might.

As Bung Sain was busy retreating and parrying, it was clear that Young
Expert Wang had the upper hand.

"What the? He's actually pretty good at fighting?"

"I did not expect him to be hiding such skills. But the true power of
Kunlun has yet to be revealed. After all, how can one discuss the
victory and defeat of a Kunlun Sect martial artist without taking into
account the divine footwork of a dragon, freely roaming the rugged
Kunlun Mountains?"

"Hm. Is that all there is to it……?"

And so, the sparring match gradually became more fierce, lasting over
thirty exchanges.

At this, Qing spoke again.

"When in the hell is this 'true power' going to be displayed?"

"Oh my. I am truly ashamed."

Jegal Ihyeon's insight was the best amongst musclemen, but it seemed
he still couldn't break the limits of musclemen.

The Daoist Bung Sain's sword stuck firmly in the center of the chair!
Young Expert Wang forcefully twisted the chair and pushed it, causing
the sword, unable to withstand the pressure, to snap.

"Winner, Wang Bang of Namnyeong!"

With that, the crowd was split into joy and sorrow.

If Qing's sparring result was the greatest upset of the sparring meet,
this match was the second greatest upset. As such, there were again
many who lost a fortune on their stakes.

"As I thought, betting against the odds is the way to go. See, I've earned
seven nyangs while sitting here."

"To be precise, it's not seven nyangs but six nyangs and eighty-nine
mun, Sister."

"Jegal, how shameful. Accept your defeat."

At this, Jegal Ihyeon let out a disgruntled sigh.

"Kuk. How can human intellect be defeated by a beast's savagery!"

"You should thank Hyang, Jegal. If it wasn't for Hyang, you would have
been hit with a beastly strike."

"Hah. I now realize why I brought Ah Hyang along with me, ack!"

"You just had to invite a beating."

"But how was it possible to strike the top of my head with such a
devastating blow from this angle……!"

It was thanks to the continuous practice of the Joint Flexibility
Technique.

Since the range of motion of her joints had expanded, the angles and
reflections of the nuclear attacks from the Ximen style had also
expanded by a significant margin.

Well, it seemed there was some benefit to bearing through the pain, she
thought.

Besides learning about the weakness of the White Hand Demonic Arts,
there was a positive side to it after all.

Qing's beautiful white hands were tough enough to endure a sledge
hammer, but she was helpless when it came to twisting joints.

Right, the next training was in seven days……

Qing's eyes slowly lost their luster.

Even if one was a master of martial arts, such torture- No, it wasn't just
like torture. It was actual torture.

Moreover, it was extremely detailed torture where they would precisely
break her joints halfway and tear the tendons about eighty percent,
only leaving them barely attached.

"Sister?"

"Ah. Uh. Yeah. Why?"

"Are you going to bet against the odds this time as well?"

While Qing was trembling, a few more matches had passed. This time, it
was a match between a disciple of the Gosan Sect and a nameless
martial artist, Young Expert Oh.

"Of course. A man must go straight forward once they have made their
decision. Here. One nyang on Young Expert Oh."

And with that, Jegal Ihyeon was defeated yet again.

"To think you are called the Intellect of the Beast, yet you need to
cultivate the bravery of a beast as well. That's why you can't win because
you keep analyzing this and that."

"Kuk……! Such humiliation……!"

As the sparring meet progressed, Qing realized that the martial artists
of the Orthodox Faction were indeed kind at heart.

If one was from a particular sect or clan, their Evil Karma would be in
the single digits, or even if it was low, it wouldn't exceed fifty points.

However, the martial artists who participated without any affiliation
and passed the preliminaries possessed Evil Karma that was in the late
teens, barely avoiding a triple digit number.

From Qing's self-set standards, they weren't necessarily evil, but they
were probably close to being a wannabe evil person.

"By the way, wasn't this sparring meet supposed to be for only the
young martial artists of the Orthodox Faction? Did they just accept
anyone who applied, even if they studied alone?"

"What are you saying? Even if they are martial artists with no
affiliation, they are chivalrous individuals who are well-known in their
region of activity, passing thorough verifications."

"Is that so……?"

If that was the case, why is their Evil Karma so high?

Of course, it wasn't like others could see the Evil Karma as a number,
like Qing.

The sparring meet was a series of upsets.

The victories of the martial artists who had participated without
affiliation and passed the preliminaries (while they were called
unaffiliated martial artists, they could also be considered ronin,
though ronin wasn't exactly a derogatory term, it had a somewhat
negative connotation) continued.

It also meant that Jegal Ihyeon continued to lose, and that many who
had tried to earn money with safe bets had also lost.

Thanks to that, the atmosphere at the venue was growing more and
more gloomy. In fact, there were quite a few who were almost crying
and didn't know what to do.

Then, it was finally time for the match of the Shaolin disciple, Wolbong.

"Sister, are you going to bet against the odds this time as well?"

"Hmm. I don't know. Hey there."

Qing grabbed a vendor who was just passing by and asked.

"What are the current odds?"

"It's three to one for Monk Wolbong."

"What?! Three to one?!"

Qing asked again.

Three to one was a pitifully low betting rate. If you bet 10,000, you
would only get 30 more.

"You are mistaken. It is eight to one. It's eight hundred and twenty to
one for Young Expert Son of Sincheon. How about you try to turn your
life around at this opportunity?"

"Nah. It's okay."

Underdog or not, there was no reason to bet on a match that made no
sense.

As there weren't many who were willing to bet on Young Expert Son, the
merchant let out a deep sigh before walking away, with his back turned
and shoulders hunched.

"Hm. The odds are going crazy."

"After all, if one were to be a Shaolin monk with the title Wol, it means
that they are disciples of Master Wunue. It's only natural when the
disciple of the Greatest Under Heaven enters the ring. So, are you not
going to bet on Young Expert Son this time?"

"My teacher said he's going to be my opponent in the semi-finals. So,
that means he will for sure make it. But what do I even get by buying a
ticket with a three to one ratio?"

At that, Jegal Ihyeon's expression stilled.

"Sister, how can you say two different things with one mouth? You
clearly said that a man must go straight forward once they have made
their decision, kuk……!"

Jegal Ihyeon gritted his teeth, seemingly aggrieved.

"Hah. You are still far from it. Didn't you experience this once in
Luoyang as well? I think I said something similar."

"That time, Brother Peng was the one who was on the receiving end. Not
me."

"But didn't you learn anything from watching then?"

"Kuk……!"

Jegal Ihyeon made a show of being aggrieved yet again.

At that moment, the Shaolin disciple, Wolbong, appeared in the
sparring arena. At this, cheers erupted from all around.

-All Martial Arts Originate From Shaolin!

-Disciple of Master Wunue!

-Successor of the Greatest Under Heaven!

At that, Qing felt a slow surge of indignation.

What the hell? When I came out, you didn't say anything, and after I
won, you booed me, but now you're so enthusiastic?

Regardless, she didn't hear the high-pitched screams that came from
women.

In Qing's opinion, it must have been that the monks were bald, as was
their characteristic.

As it could be seen from the odds, the result was already set from the
start, so it was more like a demonstration match than an actual
sparring match.

Merely with his basic movements, he swiftly narrowed the distance and
seized the advantage of fist techniques.

By retreating back and giving up that carefully gained advantage, he
seemed to be giving his opponent the chance to display his martial
arts.

Even Ximen Surin had asked her to spar for at least ten exchanges before
deciding on a winner.

As such, there was nothing for Qing to learn from this match.

From Qing's perspective, it seemed like the lines drawn by his martial
arts were all straight.

"He's so linear."

"Since Shaolin is where all martial arts originate, and it is said that they
have embodied the basics of martial arts, wouldn't the fundamentals
of martial arts naturally be like that? Stronger, faster, and more
efficient."

"The first martial arts were the Yue Maiden Sword Method, though. Then
wouldn't that be the fundamental source, instead of Shaolin?"

"The Yue Maiden Sword Method is merely a form, a mimicry of
movements without any true meaning. Therefore, rather than the first
martial arts, it would be more correct to call it the first martial
technique."

When Yue Nu taught the Yue Maiden Sword Method to the soldiers of
the Yue State, there was no concept of martial arts, much less even
martial techniques.

As such, they could only imitate its outward appearance without
understanding the function of the moves.

Yet, even with that, the soldiers of Yue possessed the power of
hundreds, easily overwhelming their opponents.

And this was when the term sword technique, the art of the sword,
first appeared in history.

Even now, the Yue Maiden Sword Method was one of the most easily
obtainable martial arts.

Of course, the fake version that the masses learnt was completely different
from the genuine body-form that Qing had mastered.

In the midst of that, Wolbong neatly ended the spar after fifteen
exchanges.

Jegal Ihyeon evaluated Wolbong's spar.

"I thought it might be an opportunity to witness the martial arts of
Shaolin, but it was settled with the Six Harmony Fist. It is truly
disappointing."

"Six Harmony Fist? The one they sell on the streets?"

Qing also knew the Six Harmony Fist.

She had learned the white-outlined martial arts that were so easily
obtainable for a cheap price. As such, the common Six Harmony Fist
was also among them.

"Shaolin's version of the Six Harmony Fist must be much more
sophisticated and profound, but since Shaolin's Six Harmony Fist had
become so widespread, the forms must not be too different."

Furthermore, he added that most of the common fist techniques that
were easily obtainable on the streets were degraded versions of the
basic exercises of Shaolin's Seventy-Two Supreme Arts. He said that
the saying, 'All Martial Arts Originate From Shaolin', was clearly true, at
least for punch and kick martial artists.

"Hm. It seems I haven't seen any real martial arts after all. I might
know more if I fought them myself."

In the end, Jegal Ihyeon did not see the martial arts that he had
mentioned as a note for introductions of the Shaolin Sect.

Where did the legendary Purple Divine Arts like Arhat Divine Fist,
White Lotus Divine Fist, Kasaya Subduing Fist, Eighteen Arhat Palm,
Almighty Vajra Palm, Hundred Step Divine Fist, Finger Flicking Divine
Technique, Vajra Finger, and the Nine Grades of Divine Force all go?

Instead, he just saw the Six Harmony Fist, for fuck's sake.

And so, the second day of the Hidden Dragon Sparring Meet, the Round
of Sixty-Four, came to an end.

Since a sparring meet was not a series of continuous lights where one
could fully display their skills, the schedule was usually a bit lenient.

The next schedule was four days later, so the Round of Thirty-Two was
to be held all in one day. Until then, they could just continue to practice
with the painful clothing and get used to the feeling.

By then, everyone would be done with their family duties to some
degree, so she thought that the Half-Sword Double-Dao Society could
reconvene.