\chapter{The Hidden Dragon Martial Arts Tournament (6)}

Since the Wulin Tournament was being held, the members of the HalfSword and Twin Saber Society also slowly gathered at the Heavenly Martial
Pavilion.

The first president was Ximen Qing, who had been appointed president of
the group that was created without her knowing.

"But if it's the Half-Sword and Twin Saber Society, shouldn't it be called the
Dao and Sword Society? Why are you acting like the dao wielder has
yielded?"

"After all, if a stranger were to hear it, wouldn't they hear the sword
first? I don't want to go through the trouble of explaining an
embarrassing name, so we agreed to put half-sword first."

"What, are you embarrassed by the name, Half-Sword and Twin Saber
Society?"

At that, the members nodded indifferently.

The name was something they had impulsively decided upon in the heat
of the moment when they were teasing each other about their weapons,
so it was only natural for them to be embarrassed.

To begin with, the act of martial artists looking down on other's weapons
was childish in the first place.

At any rate, the Wulin Tournament was not a particularly appealing
event for Qing's friends.

There was the most beautiful man under heaven who found groups
uncomfortable (he had no friends), then there was Peng Choryeo (no
friends) who had nothing to do since he wasn't a Rising Star.
Then there was the Sword Lunatic (no sword brothers) who would
rather swing his sword another time rather than waste time at the
Wulin Tournament, as well as Gonsun Yoye who had no friends, and Tang
Nanah, who likewise had no friends and was very ill-tempered.

When Qing thought about it, each of them had a flaw, making them all
friendless.

As such, it was her fate as someone who had many friends to become
the president to lead these lonely souls.

However, it was hard to catch a glimpse of Jegal Ihyeon.

After all, he was an ultra-extroverted musclehead who enjoyed mingling
with people, broadening his horizons (eavesdropping on all kinds of
stories) as his greatest pleasure.

As such, they sparred together, ate together, and went on night
outings while bathing separately.

Then, four days passed in a lash and the day for the Top 32 of the
Hidden Dragon Competition finally came.

For the past four days, Qing had been wearing the same clothes that
looked as if they were made from a blade.

At night, her body would turn red and swell from being rubbed, but
even so, her skin, which had transcended the limits of human
endurance, remained undamaged.

Just like what Cheon Yu-hak had said, once she got used to it, the pain
wouldn't be bothersome; the term 'getting used to it' was perfectly
it for this case.

Continuing to repeat the same pain would not reduce the pain, but as
she got used to it, she somehow began to feel even a sense of
refreshment despite feeling the same level of pain.

It was similar to the pleasure of pressing down on a mosquito bite with
one fingernail to leave behind marks of the Chinese characters, 口口,
十十, 田田, or the tingling sensation of one's bladder when slowly and
carefully scratching the skin next to a scab.

However, in the martial arts tournament, she had to wear the Divine
Maiden Sect robes to show which sect she belonged to, so Qing tried
them on her bare body without any undershirt, before coming to a
conclusion.

Agh, shit, seriously, this feels awful.

I expected it to be a bit more bearable, but now I can tell I haven't
adapted to the smooth texture, as I've only been wearing rough
clothes.

However, she did not frown like before.

After all, she was on the path to overcoming the pain of rough clothes,
so she would eventually get used to soft clothes as well if she spent
enough time on it.

In the end, Qing wrapped her arms and legs with arm warmers, and then
secured the robes tightly to her torso with a wide belt.

And now, it felt as if she was about to go crazy because of the utter
suffocation!

Since she had wrapped her entire body with the same stifling sensation
as if she had gloves on her hands, it was only natural.

Not feeling the wind that had always wrapped around her made her feel
as if she was about to choke.

As such, she couldn't help but rearm her determination to adapt to this
sensation as quickly as possible.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Hidden Dragon Competition was a series of unexpected events.

The win rate of wanderers, or in other words, unaffiliated martial
artists, had become so high that it was verging on the ridiculous.

Of the previous contestants, there were thirteen who were unaffiliated
martial artists. And among them, ten had reached the Top 32, meaning
that they occupied a whopping ten out of the thirty-two spots in the
main rounds.

Thanks to this, there were several spectators who lost all their
money, taking out loans and ending up in debt, as well as utter ruin,
due to being so enraged and greedy.

However, the selling of betting tickets was a legal business that was
recognized by the law and permitted by the Wulin Alliance. As such,
all responsibility laid on the shoulders of the reckless and greedy
masses who tried to make a quick buck.

After all, with the exception of a small portion that was used for
operations, the money was transparently distributed, so while
someone's tears turned to blood, someone else was bound to have
gotten rich.

And as the upsets continued, three unaffiliated martial artists in the
rounds before Qing's match, managed to advance to the Top 16.

There was that Master Ma, who used Ground-Striking Fists, and Master
Wang, who used a chair, and also that whatchamacallit, whomever. I
don't care.

After watching the matches, Qing frowned deeply.

What the fuck? What did they do for the past four days for them to
become such bad people?

Compared to four days ago, the unaffiliated martial artists' Evil
Karma had increased by about thirty points.

Unless the unaffiliated were gathering together and doing bad things as
a group, how could their Evil Karma rise so similarly?

However, there were no news, and in the first place, they couldn't
possibly cause any havoc in this Kaifeng City, where there were so many
Transcendent Masters and Ultimate Masters, and Super-Ultimate
Masters.

Just as Qing was heading to the waiting room, another snort, a rough
exhalation of air, reached her ears.

At that, Qing answered.

"Yes, I am doing well as always. Is Young Lady Moryong also in good
health?"

"Hmph. Why are you acting so friendly."

Still, she hadn't started a quarrel first. She seemed to have taken Qing's
advice to heart, realizing that the more she clung onto other's sizes,
the more she would only highlight her own feelings of emptiness.

And as she turned her head away stubbornly, a wicked smile suddenly
appeared on her face as she spoke.

"Very well. Young Lady, did you know that if you win this match, you
will have to fight me? Why don't you win against a proper opponent
and come up to fight me with your skill? Since we have a lingering
grievance, it would be rather dull to go at each other without a bet.
Why don't we make a bet each?"

"Young Lady Moryong. I do not have any lingering grievance with you.
After all, as the old saying goes, it's the one who got beaten that cannot
sleep."

"……?"

Moryong Juhee was taken aback for a moment.

According to the old saying, wasn't it supposed to be the opposite?

However, the old saying that the one who had beaten another could
sleep soundly while the one who had been beaten couldn't was a
strange saying whose existence, frankly, made no sense.

After all, the one who had been beaten quickly forgot and lived happily,
while the one who had been beaten would be tormented by injustice,
thus being unable to sleep.

"Ha. I have a lingering grievance, so I will have to make a bet. If Young
Lady Ximen loses, why don't you remove your veil in front of all the
spectators and reveal your face?"

"Hmm. Why would I do that?"

"What, you don't have the confidence to win?"

Qing couldn't help but snort in laughter.

What kind of childish provocation was that?

"Very well. If that is what it takes to ease Young Lady Moryong's mind, I
will gladly accept. Is that enough for you?"

After all, Qing had nothing to lose.

If she won, all would be fine.

And if, in the one in a hundred million chance that she suddenly lost due
to some lightning strike from the sky, she could just reveal her face.

At that, the other candidates in the waiting room gave Moryong Juhee a
rather unpleasant look.

"Again, again. You always do that, making me look like the bad one……!
Just you wait! I will definitely crush your nose!"

Moryong Juhee huffed, leaving her seat and exiting the waiting room first.

Since she was uncomfortable remaining there, it seemed she would go
down below the arena first.

However, unfortunately, the intense battle between the two prideful
women, where Qing's veil was on the line, never occurred.

Moryong Juhee, who had vented her anger on Qing, ended up losing to
an unaffiliated martial artist in the following Top 32 match.

Qing could only be incredulous.

What the hell? She said I should come up to her and then lost and went
down?

What was that? Was that that 'honorable death' thing or whatever?

And then, it was Qing's turn.

Having gone once already, she smoothly traversed the familiar
passageway before once again soaring gracefully and landing on the
arena, where she was greeted by the loud cheers of the audience.

-The Veiled Sword Maiden has appeared!

-Boo! You ugly bitch! Show us your face!

-I bet on you this time, so you better do well! If you're an ugly bitch,
you should at least be good with a sword!

After grabbing onto a few of the words being shouted with her superhuman hearing, she roughly understood the sentiments of the
audience.

Hmmm. Maybe I should just lose?

However, what good would it do to fight with the audience?

Qing simply shook it off and faced her opponent.

His Evil Karma was ninety-six points. Wow. That's barely enough.

If it were just four points higher, it would be a kill.

Completely unaware of the sinister thoughts Qing was having, the
opponent took a respectful clasped hands pose.

"I am Do Raeman from Simcheon. I have learned the Danyang Dao
Technique."

"I am Ximen Qing, a disciple of the Divine Maiden Sect. I have learned
the Divine Maiden Sword, Yue Maiden Sword, and other miscellaneous
techniques."

In fact, she didn't have a decent way of using her left hand in the match.

Although she could always say it was just the way she fought, it was
rather too much to openly use the White Hand Demonic Arts or the
Black Slaying Demonic Palm, and the Shadowless Divine Step was a
secret.

The Buddha's Palm was too powerful and she could only use it as the
Buddha-Style Noogie, severely weakening its power or completely
bursting the torso.

And if she were to wield weapons with both hands, a dao technique was
also Demonic Arts, and using two swords would not let her win, so
using twin swords was out of the question.

Just look at Moryong Juhee, who had challenged her to a duel.

She was a woman famous for using twin swords, which had revealed her
limitations; if it wasn't for the twin swords, she would have been able
to fight Qing in the next match.

"Since my realm is not low, I shall concede the first move. Go ahead,
come at me."

"I shall not refuse."

Do Raeman nodded in thanks and charged at her.

What the heck?! He's fast!

In the blink of an eye, Do Raeman's body, having swung his blade
greatly, had arrived.

Qing was surprised and bent her knees in the Iron Plate Bridge
stance. Her body lay horizontally, and swoosh! A bladed edge,
though it was blunt, cut through the air.

Qing then pushed off the ground and rolled backwards, doing two
cartwheels before standing on the stage.

And then again, Do Raeman was right in front of her with a sword that
had soared high into the sky and was now glistening.

Qing stepped on the positions of the Nine Palaces, causing her image
to multiply into six while disappearing and reappearing nine steps
behind Do Raeman with her back facing him.

The absolute Masters of Wulin, watching from the wooden pagoda at
the front of Kaifeng, jumped up and shouted in unison.

The Ripple Step!

Regardless of all that, Qing reflected.

Wow, he's really fast.

Among all the martial artists I've fought so far, he's a top-tier
swordsman when it comes to speed, no, a dao wielder.

So, this is what it meant by the world being wide and big……

Qing, who had inwardly looked down on him for being an unaffiliated
martial artist, was nearly struck after conceding just one move.

Qing turned her body quickly while Do Raeman, who was also
bewildered at losing sight of her, quickly found Qing again.

The defining characteristic of the Ripple Step was that it was
specialized only for evasion and escape.

Do Raeman's martial arts were all about aggression.

Based on his fast speed, the trajectories of the dao he swung with both
hands held a destructive force that felt as if one would be sliced into
two if they were hit, even if it was a blunt, training dao for sparring.

However, she now knew his speed.

It was an intense strike with fast speed and precise targeting, but it
was honest without any guile, thus revealing its trajectory.

However, such an intense strike was hard to parry even if she saw it,
so his understanding of martial arts was, to say the least, quite
profound.

But Qing was not one to back down in a head-on confrontation.

Qing, who was holding her sword with both hands, slashed upwards
with a wild swing, causing a clang! A metallic sound echoed as Do
Raeman was sent up into the air.

In fact, there were hardly any Moves for cutting from below in
swordsmanship or dao techniques.

The inverse movement of going from the earth to the sky required
several times the force compared to the opposite direction.

However, once one had that several times the force, there was no other
technique as powerful as this.

Due to the natural principle of action and reaction, Qing transferred
that force to the ground, while Do Raeman lost his weight and was
sent into the air.

Now, I should let him go at least ten moves.

Qing, who always listened to her teacher, lowered her sword rather
than chasing after her opponent in the air.

Having landed on the ground, Do Raeman took another two steps back
and regained his balance. Then, he raised his left hand in front of his
chest to express his gratitude, even while in the middle of a match.

Qing felt a bit confused.

What the heck? Why is he so polite? He's not a bad guy, is he?

Then why is his Evil Karma like that?

Do Raeman had a much more relaxed expression.

He had realized the difference between himself and Qing after that one
move.

While also acknowledging her intention to give him a chance to
showcase his martial arts, he calmed his competitive spirit and adopted
an attitude of simply showing his best.

At that, Do Raeman's dao technique changed.

Gone was the intense strike that was tied to speed, replaced by a
heavy and forceful dao technique that was wielded with a stomp on the
ground.

Moreover, the sudden bursts of speed mixed in every half-step
made it quite threatening, but Qing, who was no longer looking down
on her opponent, easily dealt with them.

As such, ten moves passed, and then the eleventh.

A dao qi with the nature of extreme yang swung around, as if to cut the
sun, drawing a large semi-circle, and by the time it passed, Qing's blade
was already touching Do Raeman's chin.