\chapter{The Hidden Dragon Martial Arts Competition (3)}

Since Cheon Yuhak had gone off to do his own business, Qing was left to
wonder what to do. But then, with her signature lack of hesitation, she
tracked down a large dry goods store after asking around.

It was because she had been completely convinced by Cheon Yuhak's
words that it was meaningless to keep it covered if it was hard to
endure, and also because, now that she was out, she wondered if there
might be suitable clothing to wear.

"What kind of clothing are you looking for?"

"I'm looking to buy some cotton cloth. Do you have any high-quality
ones? The highest quality."

"Ah, you've come to the right place. As it so happens, we just received
a precious product that uses 180-count, 6-ply thread. Would you like to
take a look?"

180-count referred to the thickness of the thread, with higher numbers
indicating a thinner material. 6-ply indicated how many strands were
twisted together.

In other words, the clerk meant that it was cotton cloth woven with
six strands of very thin, 180-count thread.

"Oing? Something like that exists? May I take a look?"

"Of course."

Just hearing that it was cotton cloth made of 180-count, 6-ply thread
was enough to know that it would be incredibly soft.

When Qing actually touched the fabric the clerk brought out, it was
indeed so. It was light, soft, and no different from silk.

However, it was also an ambiguous product.

If that was the case, it would be better to use silk instead.

"It's nice. How much is it? How much do you have?"

At that, the clerk's face lit up.

Such a big customer!

Qing, who was not particularly frugal, bought all the expensive cotton
cloth and wandered among the clothes hanging in the shop.

"Customer, is there a certain type of clothing you are looking for?"

"Just looking around."

If you translated 'just looking around', it meant, 'I'll look around on my
own, so don't talk to me'.

The clerk stepped back with a regretful expression. Then, Qing looked
over the clothes.

However, since she had never cared about clothing before, there was no
way she would know. When she looked at thin clothing, it was all full
of things that seemed too embarrassing to wear. But at the same time,
her Master's words kept gnawing at her mind.

While she was hesitating like that, she suddenly saw a particular
garment.

Oh. What's that?

It was a coarse linen garment that caught her eye at a glance.

"Hey, that linen garment over there is……"

The clerk, who had been watching the big customer with regret,
rushed over eagerly.

"Hehe, that's quite a unique garment, isn't it?"

As the clerk explained, it was a dress ordered by the wife of some
high-ranking official. It was originally created as a mourning dress, but
before the garment was finished, the woman had run off to get remarried.
Because it was a garment woven with the highest quality of linen, it
couldn't be thrown away. So, they dyed it and hung it there.

"How is it? Isn't the black color subtle and beautiful? There's not a
single imperfection or fray to be seen in the linen, so you can see how
skilled I am with color. If you have any clothes you want to dye……"

After hearing the explanation, Qing realized that it wasn't a garment for
sale but a signboard to boast of the dyeing technique.

In Zhongyuan, when someone said 'black', they didn't mean a
pitch-black garment like in Qing's hometown.

They meant dark gray, the same color that modern mothers would
describe as dark mouse-gray.

It wasn't completely black and it gave off a bright feeling, but since its
base was black, it couldn't be too bright either.

As such, a properly dyed black color had a very elegant and graceful
impression.

The color was indeed beautiful, but that was it. Qing had a thought
that suddenly struck her mind.

Qing's eyes shone as she asked.

"How much is that one?"

From its origins, mourning clothes were created to be uncomfortable.
Losing a parent, teacher, or an unhelpful monarch meant that one had
no way to prove that they were in pain and grief except by showing off
their sad and uncomfortable state.

As such, the garment created to show off to all under heaven that the
wearer was indeed uncomfortable, regardless of their inner feelings,
was precisely the mourning garment.

However, due to how luxuriously it was dyed, it didn't feel like a
mourning garment at all.

But that discomfort was real.

"Kuhhh……"

Qing's idea was simple.

If being happy was a problem, wouldn't it be okay to just become used
to the feeling of being unhappy?

Since the softness of silk as it brushed against her body was too
excessive, wouldn't it be better to wear linen that scratched against her
skin instead?

As such, she tried it on with a pounding heart, only to go, woah, this,
is, AAAAAAAAAAGH.

Originally, linen fiber was rough and stiff, but if it was soaked in starch
and repeatedly rubbed to release the starch, the stiffness would
disappear, but sharp hooks would form on the threads, making it even
rougher.

In addition to that, it had been dyed.

Rather than dyeing the thread, the already woven garment had been
dyed and chemicals were used to preserve the color. So naturally, it
became even rougher.

As such, the result was closer to steel wool than fabric, or even more
rough, closer to a wood-carving plane, what was known as sandpaper in
Qing's hometown.

It was as if she had made a garment out of sandpaper when she had
skin that was as sensitive as her fingertips.

The stinging sensation made it feel as if her skin was being grated away
every time she moved her body.

"It's a bit, too… from the very beginning, it's practically at the
extreme."

But still, it was better if it hurt.

Every time she moved, her skin was scraped raw, making her scream,
but it also sharpened her mind, making her consciousness clear.

Moreover, it was a garment suitable for training.

Linen was originally a well-ventilated garment that allowed air to flow
through.

Moreover, when the stiff top got caught on an obstacle and fell
straight down, her stomach floated up by two fists' width, allowing the
wind to freely pass through.

As it was slowly getting hotter, she had to at least appreciate how cool
it was.

"Tuhaaaaak."

All she had to do was become accustomed to the uncomfortable,
aching, and painful feeling, she thought.

According to Cheon Yuhak, there was no particular training method for
the art of reading space through the senses of the skin.

It was a result of a collection of experiences that accumulated
unconsciously.

If she lived for a year or two while the wind was passing through her
skin, it was said that her vision would naturally expand in all directions,
allowing her to know what was behind her based on the air currents.

If she wanted to shorten that time period, she would have to go around
naked. As such, it was important to wear something that allowed for
maximum air circulation and travel to as many places as possible.
By doing so, she would be able to greatly shorten the time it took to
expand her senses by experiencing strong and weak winds, crowded or
complicated places, and enclosed spaces.

Of course, that was still a distant matter for Qing.

She was not even accustomed to her current senses, so how could she
have any time to care about the wind or anything else?

While wandering around the streets of Kaifeng at night, Qing thought.

It feels like my skin has all been scraped off. Is blood even flowing,
perhaps? I wish I could just give up and go to sleep.

But even while wearing a grimace, she wandered around until late at
night. So somehow, she was holding on.

Therefore, Qing had no other choice but to feel proud of herself.

Wow, today was so fulfilling too.

Almost every moment of my life is training, huh.

This kind of hollow pride was actually closer to self-consolation, which
was never a good thing.

But still, it was much better than a completely escapist attitude of
playing, eating, and enjoying oneself, so she could say that she had
become better than before.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Grand Assembly was a meeting where the high-ranking members of
the Martial Alliance gathered to discuss the future direction of the
organization.

Although anyone could participate in the Grand Assembly during the
Martial Arts Competition, the truly important matters were decided in
these gatherings of their own kind.

In this meeting that felt like a gathering of dark forces, Ximen Surin
strongly asserted.

"How long are you going to keep tolerating those black spot bastards?
As their depravity worsens with each passing day, is it really okay for
the righteous Martial Alliance to leave them be?"

As a former high-ranking member from the previous generation, Ximen
Surin's manner of speaking was bold and unrestrained.

Perhaps for that reason, the expressions of those listening were not
bright.

"But Senior. Not everyone in Black Spot is a bad person, right? There
are many ordinary citizens who rely on them for their livelihood. How
can we recklessly attack them and create chaos?"

While the Black Spot was a hotbed for all kinds of dirty dealings, it was
also a lifeline for wandering peddlers who had no shops.

The people who gained courage from that added their own opinions.

There were many martial artists from the Orthodox Faction among the
customers of the Black Spot. If it was eliminated, they would find it
difficult to evade the government's eyes or quickly obtain rare items.

The Black Spot wouldn't cooperate unless they went too far or became
enemies of Wulin. Since they had a firm grip on the underworld
bastards, they could be easily apprehended at once.

The emphasis was placed by Martial Arts Master.

"Daoist Ximen, then, how do you think we should deal with the Black
Spot? They are not the kind of people who would stop just because we
tell them not to. We cannot imprison them in a Repentance Hall to
reeducate them, nor can we just massacre them all."

"Hmph. What is it that we cannot massacre a bunch of scum? If you are
going to spout such old-fashioned nonsense about not killing, then-"

"Then, how far are you going to massacre? The 'I' and 'mine' forms?
Then what about their range? Would those who supply them directly, or
those who only distribute them, deserve to die? What about the receivers
of stolen goods? Should we kill the robbers who hurt people but spare
the pickpockets who only steal things?"

Ximen Surin frowned deeply.

That damned monk was always so slippery.

That honorific he used on everyone, from the start, was an incredibly
offputting serpentine tactic.

In the first place, why should there be a standard for who to kill and
who to spare when it comes to taking down bad guys?

If they are caught, they die. A lucky bastard might live. They might be
unable to get rid of their bad habits and end up being cut down by a
sword, or they might, just possibly, change their minds and step into
the light.

In the first place, the Martial Alliance was not a gathering of divine
beings that had reached the heavens, so even if they decided to create a
standard, it was not something that would be implemented to everyone.

As such, how could she possibly answer if they asked for a standard
right here and now?

It was truly a cowardly way of talking.

As such, she could only let out a deep sigh and threaten them.

"If you keep avoiding such troublesome matters, you will inevitably
cause a big incident. They are becoming more and more lax, and they
will inevitably cause a major accident someday. Once something
happens, it'll be too late. Tch. At that time, it will be a disgrace. Forget
the disgrace, how will you repair the public sentiment of all under
heaven?"

"We can just punish them if they go too far. It's not like it's the
Orthodox Martial Faction who committed depravity, so why would the
public criticize us?"

The conclusion was rejection.

"Tch."

Ximen Surin clicked her tongue.

This is why she hated coming to the Martial Arts Competition.

Regardless, the Grand Assembly continued.

"Then, the next agenda is the matter mentioned by Daoist Cheonbi.
Regarding the opening of the Martial Arts Academy…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

On the second day of the Martial Arts Competition, the Hidden Dragon
Martial Arts Competition was scheduled to have the matches of the 2nd
and 4th groups.

Qing took a seat in the audience due to Ximen Surin's request to watch
the match of the Shaolin disciple, Wolbong.

It was a request to prepare for the semi-final match by looking at the
Shaolin's martial arts, known as the greatest under heaven.

On her right was the commentator, Jegal Ihyeon, and on her left was her
friend, Tang Nanah.

And on her lap was Jegal Hyang, who was in charge of cuteness.

Qing had a lineup that was second to none. It could be said that she had
a right guardian, a left guardian, and even a pet.

However…

"Kuhk."

Jegal Hyang was a young girl who would be considered a child even by
Korean standards, so the Martial Arts Competition didn't seem to be
very entertaining for her.

She couldn't stay still on her lap, swinging her legs around and fidgeting.

As a result, the sandpaper-like fabric roughly rubbed against her skin.

Upon hearing Qing's pained groans, Jegal Hyang bent her waist backward,
tilted her head upward, and asked.

"Gaga Unni, am I heavy? Ah, so squishy."

Jegal Hyang wiggled and fidgeted, bumping the back of her head
against Qing's lap.

At that sight, Qing's heart dropped. What the hell is this cute creature?

How can she be like this?

"No, Hyangie is light. But, aren't you having fun, Hyangie?"

"Umm… A little. Haaaam."

And then, she let out a yawn.

Qing was so happy at that and embraced Jegal Hyang, letting her rest
against her.

Yes. It would be better for her to sleep.

If she kept fidgeting, I'll get scraped.

"Then just sleep for a bit. Lean on me comfortably."

"I'm not sleepy……."

Even as she said that, Jegal Hyang soon fell sound asleep.

Kids always slept quickly.

Qing comfortably watched the matches with a much more relaxed
attitude, and then suddenly tilted her head in doubt.

"Wasn't that that Little Fellow Wang? Did he always use that?"

"Did his chair change? I heard that they had to get a new one after his
chair was destroyed in the last round. Originally, chairs are weapons
strong against blades, so they are weak against dull swords, used for the
matches."

"No, that's not it……"

Qing looked at Wang, the martial artist using a chair as his weapon.

He was memorable because he used a unique weapon, and his
Righteous Karma was a single digit, either three or four or
something. What had he done for him to suddenly become such a bad
person? 
