\chapter{The Hidden Dragon Martial Arts Tournament (9)}

"Qing'ah? Where are you going?"

"I just left something behind…"

Though she didn't know much about the Blood Cult, she did know that they were terrible people. Everyone had been gritting their teeth with such animosity that it was clear they were far from good.

As such, Qing dragged her exhausted body and headed back to the bathhouse.

And there, she found Cheon Yuhak filling a bamboo tube with the leftover bathwater, whose medicinal properties had expired, from the bath that had been used for the Elixir Palace.

"What are you doing? Was that recycled?"

"Of course not."

"Then why are you putting it in a separate container? There's so much. Are you going to pour it all in there?"

The bamboo tubes were already scattered all around Cheon Yuhak, so it was obvious that the amount would exceed the amount of water in the bathhouse.

"Why do you care? Anyway, you should be tired. Why are you not sleeping?"

"That Sleeping Silk Elixir, you know? It turns out that it's made with blood essence. And you know what blood essence is……?"

"Do you think I don't know what blood essence is?"

Then, Cheon Yuhak roughly scratched the back of his head. It was a gesture that was full of annoyance.

"Seriously, this is really fucked up. That fake Divine Hand has been spreading a human elixir that deserves to be torn into pieces. What kind of bastard planned to smear shit on other people's faces?"

"Shouldn't we ask the unaffiliated martial artists? I think Dao Sohyup was quite cooperative, though."

"For now, just go to sleep. Your tendons aren't fully healed yet, so sleep soundly before doing anything tomorrow. I'm so tired right now that I only noticed you were here a long time after you came. Isn't that enough to prove how tired I am?"

In fact, Cheon Yuhak's eyes were dark with fatigue.

And the way Qing looked to Cheon Yuhak was no different.

Though Qing might not be mentally exhausted, her body was already battered. If it wasn't for the effects of the Elixir Palace, she would have collapsed from exhaustion a long time ago.

"But, still, the matter is a bit serious……"

"Hmph. What kind of big deal can happen when the majority of the Ten Great Masters Under Heaven are gathered here? It looks like they are just trying to give the Blood Cult a bad name by involving them in the Martial Arts Tournament. Blood Cult, my ass. Fucking hell."

Cheon Yuhak's weary face contorted even further.

"Let's just sleep for now. You can't do anything in this state, even if the situation is urgent, and it's not like it's really that urgent either. Tomorrow, hmm. Well, the Divine Hand matter will have to be dealt with by the Divine Hands themselves. And don't go around talking about it with others, okay?"

"Do you think I'm a child who can't distinguish what should and should not be said? You should sleep too, Master."

"Alright."

And with that, Qing returned to the Martial Heaven Hall.

But then, it suddenly occurred to her. What's with those bamboo tubes? I forgot to ask about it while we were talking about the Sleeping Silk Elixir.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since the unaffiliated martial artists were staying at the Wulin Alliance's Transient Hall, Qing did not have to wander around Gaebong in search of people.

"Come to think of it, how are you able to freely enter the Wulin Alliance, Master? Did you come as a guest?"

"Hmph. If you're wearing a simple cotton robe that servants wear, no one will question you, no matter where you go. If you also get yourself a uniform that lackeys wear, then the entire mansion will be your area."

The larger the mansion, the less likely anyone would suspect someone if they were wearing servant's clothing.

This was not because the identification process was inadequate in the primitive ancient times of China. Rather, it was because people were used to treating objects or scenes as mere backdrops when they wore a certain attire.

Even in Qing's hometown, wearing a yellow or green safety vest was enough to keep one from being suspected even when wandering around.

Since the two of them were sticking together, it looked as if Qing was going around with her personal servant.

And for that reason, no one asked who Cheon Yuhak was.

And so, they arrived in front of the Transient Hall.

The Transient Hall was a mid-to-lower level guest hall among the Wulin Alliance's guest halls, so it was miles away from the Martial Heaven Hall that Qing was staying at.

"Is Young Expert Do Raeman inside?"

After asking a servant of the guest hall, they found their way to the room. The room was not a single room, but a double room for two people.

The small room, with two beds attached to each side of the wall, was barely a quarter of the size of one of the rooms in Qing's Martial Heaven Hall.

"Young Lady Ximen? What brings you here?"

"I came to see you to talk about yesterday's incident, and it seems that this young expert uses the Palm of Subduing Earth………"

"It is called the Demonic Shadow Fist."

Since it was a double room, there was one other person besides Do Raeman. That person was Ma Yeongjeon, the master of the Demonic Shadow Fist.
Ma Yeongjeon glanced back and forth between Qing and Do Raeman and spoke with a strange smile.

"It seems you two have something to talk about. Then, I should graciously excuse myself. Young Expert Do, I didn't know you had a hidden talent."

"Brother Ma, it's not like that. Um. You don't really have to leave. If Young Lady Ximen is here to talk about yesterday's incident, then she must have come to discuss the Sleeping Silk Elixir, right?"

At that, Ma Yeongjeon's expression stiffened.

"No, look here. How can you talk about that so carelessly? I know nothing about it, so I'll take my leave."

And just as he was about to sneak out, Qing was already certain that he had taken it too.

In fact, all the unaffiliated martial artists had their Evil Karma increase simultaneously, so she was already close to certain that they had taken it.

Since he ate a person, it was only natural for his Evil Karma to increase.

Whether he knew the true nature of the Sleeping Silk Elixir or not.

Just because one didn't know about a poison didn't mean the poison would let them be. After all, once the venom entered the body, it would not think, 'Ah, you didn't know about the toxicity. Then I will especially refrain from poisoning you'.

"Do you want to hear this as well, Young Expert Ma? Yesterday, I received a Sleeping Silk Elixir from Young Expert Do, and after investigating it out of curiosity, it was a vile item made with blood essence, you see?"

"Blood essence……"

Instead of shouting out in denial, Do Raeman muttered.

Then, with a troubled expression, his face turned pale.

"I did not know. I did not know it was such a thing."

"I'm not blaming you. Since it is not something that is good to be revealed, I just want to find out who is spreading such a drug and what their purpose is. Will you hand over what you have as well, Young Expert Ma? I think we should see if it's the same thing."

"I-I know nothing of such matters. That the Sleeping Silk Elixir was made with blood essence? Young Expert Do, I didn't think you were someone like that. I am truly disappointed. Yes, truly disappointed."

At that, Qing's eyes narrowed.

"Do I really have to ask about your strange speed and strength from your past opponents to get you to hand it over?"
"A martial artist should always hide at least 30\% of their skills-"

"I know all your tricks, so just hand it over."

Qing cut off Ma Yeongjeon's words and held out her hand.

Ma Yeongjeon, after glancing at Qing's white and slender hand with trembling eyes, swallowed hard, straightened his expression, and looked her right in the eye.

"I do not know what you are talking about."

In the end, he was pretending to not know.

In reality, if they reacted like that, there was nothing Qing could do.

Without any clear evidence that they had taken the Sleeping Silk Elixir, all she had was her intuition, and to accuse them of such a thing, especially if the Sleeping Silk Elixir was made 
with blood essence, would be problematic.

And it also wasn't like she had a way to prove anything. After all, much like the proverb that said a martial artist should always hide at least 30\% of their skill, they could just insist it was their natural ability.

And even if she did say something like, "Oh, I can see people's karma", no one would believe such an absurd statement from a quack.

At that, Qing sighed deeply.

If she had no way, then what could she do?

Qing gave up on trying to persuade them.

She gave up on persuading them only.

Qing sighed deeply and suddenly sprang up from her seated position, stretching her legs out.

At the same time, CRACK!!!

It was a very crisp sound, like a walnut being cracked open!

"AAAAAAGH!"

Ma Yeongjeon grabbed his crown and rolled across the floor of the guest hall.

The power of the Divine Realm's Core Arms was so powerful that it was a terrifying violence far too early for the surface world under the Divine Maiden Peak.

"Why won't you ever listen when I talk to you? Did I seem that easy to you? Do you think that just because I act calm and docile, you can look down on me?"

"Y-Young Lady Ximen?"

"I told you I'm from the streets."

"Ah. Um. I see."

At that, Do Raeman nodded.

Though there were hardly any female ronin warriors, those who existed always had foul mouths. It couldn't be helped, it was a basic requirement for women to not be looked down upon in the ronin world.

"Young Expert Ma? Stop acting like that and just hand it over. Or would you rather get beaten up like a dog and cough it out? If you eat pills made with human remains so carelessly like that, I can be just as dog-like, you hear me?"

"Guh, what in the world do you think you are doing?!"

"Oh? Not coming to your senses yet? Why don't we have a life-or-death duel with our ancestors' honor on the line? Let's make a bet to see if a red Sleeping Silk Elixir comes out after looking through your corpse?"

Then, Qing took out the Black Serpent Whip as if it was only natural and released her True Qi for once.

Her True Qi, which was elated to be outside for once, surged out all at once, thus rapidly reaching the weapon through the sixteen-lane highways in her meridians, created by the Yijin Cleansing Method.

However, instead of the Black Serpent Whip, the Blue Serpent Sword, which had been present in its place, was drawn instead.

Thanks to that, a stream of Sword Qi with absurd power poured out of the blue blade like lightning strikes.

"Shall we see what level of skill you possess? For reference, even Transcendent Realm Masters die in my hands. If I say, 'Transcendent Realm Master, die!', even the Transcendent Realm Masters die. Do you know about the Demonic Cannibal? That guy also was too cocky in front of me, so he went ahead to say hello to Buddha. Did you perhaps hear that there is no order in which people die? Or would you like to have another Sleeping Silk Elixir, now that you've got a taste for it?"

Although her words were shocking, Ma Yeongjeon was utterly defeated in the face of her terrifying display of power.

Unlike the display he had shown in the competition, this brutal veiled woman was a true Master!

Her martial prowess was exceptional, but she was also a master of Inner Qi, who had properly built up her profound Inner Energy.

Especially in the face of her thick Sword Qi, which was not like ordinary threads, but more like a serpent, how could he possibly resist?

"I… I'll give it to you."

"You should have done that in the first place."

Qing was putting her Black Serpent Whip back when she felt a subtle prick, and upon checking, it was the Blue Serpent Sword.

Since it was a minuscule amount of the White Hand Demonic Arts, a mere grazing of the blade was enough to sting. If it hadn't been such a small amount, she would have received a major injury that would have exposed her bones.

"Oh my. There's a dagger here. My Black Serpent Whip. Hmm. I wonder when I'll get it back."

"Hmph."

Cheon Yuhak, who had been watching Qing's atrocity with a dumbfounded expression, let out an uncomfortable cough.

It was because Cheon Yuhak himself had also completely forgotten.

That he had forgotten about Qing's atrocity, let alone the Black Serpent Whip.

Come to think of it, she was the one who kicked a man's crotch at the Black Spot, lifting him up to the height of a jhang.

She was also the one who had rammed into a Black Spot merchant in the Black Spot's territory, but after meeting her again, he had forgotten all about it since she had acted like a proper lady.

At that, Qing dusted off her hands and said.

"This is perfect. We need to ask the fellow experts in the other guest rooms to gather. Young Expert Ma, would you please do us the honor?"

"Uh, what about Young Expert Do…."

"That's why, if you had confessed with kind words, you would have been able to find enlightenment. Our Young Expert Do can just rest easy."

At that, Do Raeman's face became extremely uncomfortable. He was seriously wondering whether this was bullying or if she was just giving him a look.

Qing clenched her ist and rubbed the protruding bone at the base of her middle finger as she continued.

"Okay. Young Expert Ma, no, Young Master Ma? Do you want to leave now, or do you want to receive a gentle bonk on the head and leave while bleeding?"
