\chapter{The Hidden Dragon Martial Arts Tournament (2)}

Sixty-four people were to participate in the first round of the
tournament; twenty-four who had risen from the preliminaries, and
forty who had advanced to the main round by recommendation from the
Orthodox Faction.

Today was the first round for Group 1 and Group 3, which meant that
everyone had to wait endlessly, not knowing when their turn would
come.

Qing's plan to seek out Cheon Yuhak and ask if there was another
method since the side effects of this one were so severe was now
pushed far back.

Agh, damn. I don't even know where Master is.

She had clearly heard him mumbling about selling tonics, so he was
probably somewhere in the market. But once he sold everything with
his unique and mystical salesmanship (forceful sales), it would be
impossible to find him.

And so, in such an anxious state, she was just left to watch the petty
fights of these low-level nobodies!

Hmm. It's kind of interesting, though……

It was a common theory that fights between nobodies were far more
interesting than fights between Masters.

This was because while the details of a fight between Masters were
hard to grasp, a fight between nobodies was easy to understand at a
glance, making it thrilling and nerve-wracking.

Oh, Small Master Ma of the Ground-Hugging Fist also made it.

Small Master Ma, a Master of the Ground-Hugging Fist, was on all fours
as he faced Small Master Chae, a disciple of the Returning Home Sect.

Although being on all fours usually meant one was in a position of
defeat, Small Master Ma, a Master of the Ground-Hugging Fist, was in
fact gaining an advantage due to his constant use of all fours.

The poor disciple of the Returning Home Sect continued to flail around,
completely clueless on how to attack an opponent crawling around
beneath his knees.

Well, to be fair, there wasn't any known martial arts that had a stance
for dealing with an opponent crawling under one's knees.

And so, Small Master Ma burrowed in like a snake, pressing on the back
of Small Master Chae's knees, thus tangling up his feet and taking him
down.

And then, Small Master Chae tried desperately to break free, but each
time he did, he could only suppress a scream because of the pain he felt
as if his bones were being crushed.

The martial arts alliance master, who was the judge, watched the
Returning Home Sect disciple's escape attempt a few times before
quickly making a decision.

This wasn't a biased ruling; it was to see whether there was any
possibility for the restrained disciple to break free through some
method.

"Match! Ma Onsa from the Divine Maiden Sect Wins!"

Cheers erupted from the crowd.

Small Master Ma waved his hands happily, and the poor disciple of the
Returning Home Sect hung his head low and walked away.

At the very least, they needed to show something that looked decent
during the tournament, but even that was impossible since he had been
matched against the wrong opponent.

"Tsk tsk. How vile. How can he walk around with his head held high? But
I can't tell that child to stop using the Ground-Hugging Fist either."

Ximen Surin said with a look of sympathy.

Ximen Surin had previously asked her to endure at least ten rounds, no
matter how low the opponent's realm was, or how terrible their skills
were.

This wasn't a stage for life-or-death duels. It was a good opportunity for
the Orthodox Faction disciples to show off their skills, thus requiring
them to at least give their opponents an opportunity.

Although Small Master Ma had won and gained renown, all that meant
was he was a Master of a horrible martial art that involved crawling
around on the ground. And the loser had become a worthless fool who
could not even defeat a Master of such a vile martial art.

Even if they win, they don't really gain anything, and the disciples of
the Returning Home Sect would hate Small Master Ma, gaining him
nothing but grudges.

The reason why the Ground-Hugging Fist was avoided in Wulin was
because it had so many downsides that were continuously spewing
forth from every angle.

After that, the matches continued, and familiar faces would appear
from time to time. Gongson Yoye had easily defeated Shang Baeksong of
the West Sky Commerce, and Jegal Ihyeon had used his iron fan to knock
out some guy from Qinghae.

And then, Qing's turn was suddenly upon her.

The martial arts alliance member in charge of the proceedings guided
her to the waiting room, saying her match was coming up soon.

The waiting room was a ship that had been docked and raised on the
tournament venue on the canal, and as soon as she entered, a snort
rang out.

It was more of a snort than a snicker, so Qing looked at the source of
the sound.

"Ha! It seems Young Lady Ximen is revealing her true colors? What is
that attire of yours?"

In fact, there was only one person who would start trouble with Qing
upon sight.

Moyong Juhee pointed her finger at Qing.

"What is that gaudy sash, I ask? It seems you are trying to show off your
figure to the entire Zhongyuan. At that rate, wouldn't it be better to
just take off your shirt?"

Sash refers to a woman's belt. Unlike Qing's hometown, there were a
variety of belts in Zhongyuan. If it was just wrapped around the
waist outside of one's clothes, it was called a sash.

Qing had tightly wrapped her waist with a wide cloth to prevent her skin
from brushing against the rough fabric.

She already had a thin waist with an overly thick upper and lower body,
so the huge difference between those curves was clearly visible.

Qing let out a deep sigh.

Was this her weird way of greeting people or something?

"Young Lady Moyong, isn't it tiring for you to start trouble with
everyone you meet? If you say such things, everyone will start to make
comparisons. Hey, everyone, wouldn't you mind averting your gaze, so
as not to be rude?"

It was exactly as she said. The other people waiting in the waiting
room were all looking back and forth between Qing and Moyong Juhee.

"Tsk…!"

Moyong Juhee bit her teeth with a scarlet face and fiercely swept her
gaze over the contenders waiting in the waiting room.

The contenders in the waiting room put on embarrassed expressions
and pretended to be thinking about whether there was a strange
pattern on the floor, walls, or the ceiling.

That's when it happened.

"KYAAAAH!"

"KIYAAAAH! KUUAAAAK!"

Suddenly, desperate screams rang out from outside the waiting room.

It was a heart-wrenching scream that felt like tearing the liver apart.

The surprised contenders in the waiting room jumped up and looked
outside.

And then, outside were…

"KYAAAAH! Young Master! Young Master Peng! Please look over here!
KYAAAAH!"

"Jade Qilin! KYAAAAAH!"

"Oh my, I made eye contact. What should I do, ahhh…"

Thud. Women started falling down one after another.

The most handsome man under heaven was able to destroy the minds of
women with a single glance and make them faint.

Even after a few bad rumors recently, his popularity hadn't died down
at all. In fact, there was a series of women in Kaifeng wearing tattered
clothes, emulating the style of beggars, to get his attention.

What the hell? I got needlessly startled…….

Qing sat down in her seat, feeling listless.

Surprisingly, Moyong Juhee frowned and turned away as well.

As Qing turned her veil to face her, Moyong Juhee frowned deeply.

"Why are you doing that? Isn't it amazing that I'm not looking at the
most handsome man under heaven? How hilarious. Do you think I'm
pathetic enough to cling to a man that says they don't want me?"

"I didn't say anything."

"Your eyes said everything?"

"Can you see my eyes? Are you a Master of the Unrestrained Realm or
something?"

Qing didn't understand the principle behind it at all, but apparently,
if you were a Master of the Unrestrained Realm, you could see through
even someone wearing a veil.

"Tch."

Moyong Juhee turned her head away as if she didn't even want to
bother with her.

Qing didn't want to bother with her either, so she just let her do what
she wanted. She didn't think they would be seeing each other again
anyway.

As she was thinking that, another round of crazed screams rang out.

Since she had already experienced it once, she knew without even
looking.

It seems Sanie won, huh.

After that, it was Moyong Juhee's turn, so she was guided to the
passageway. Not a moment later, the host's voice announced Moyong
Juhee's victory!

And then it was finally Qing's turn.

As she followed the inside of the ship, crossed a few planks on the
dock, and headed into the interior, she came to a set of stairs with a
handrail and a platform.

So that's why everyone was leaping up from the floor, trying to gain the
upper hand with their Lightfoot, huh?

If there was a platform with a handrail, even those who were weak in
Lightfoot could leap up at least a few feet.

Qing leaped up lightly on the platform using a Anti-Gravity Stroll of
the Yue Maiden, and then, she soundlessly and gracefully stood on the
tournament stage with the tips of her toes.

"I am Hwan Yook, a disciple of Wudang. I have mastered the Taiji
Divine Sword and the Flowing Palm."

And then, he showed half a stance of his sword and half a stance of his
palm as his Starting Ceremony.

Qing also responded, demonstrating the basic stances of the Divine
Maiden Sword and Yue Maiden Sword.

Then, after all that, Hwan Yook suddenly asked a question.

"Young Lady Ximen? Have we perhaps met before? You seem rather
familiar to me…"

Who is this guy? Is this some kind of joke?

Was there a pre-match custom of gaining the upper hand through
bothersome conversations in Zhongyuan, besides in the modern
age?

Qing, who never lost in that domain, retorted.

"Is that a question a disciple of Wudang should be asking?"

"Huh? What do you mean…"

Hwan Yook was confused as to what she meant, but he soon realized
his mistake.

To say a woman wearing a veil looked familiar was obviously going to
be seen as a cheap attempt to hit on her.

It wasn't that, as his gaze had just been drawn to her rare and unique
aura that seemed to be there but not really there, but that, too, was
impolite to bring up. After all, it was as if he had just said 'You have a
great figure, where have I seen you before?'.

"I apologize. Please forget what I said."

He doesn't even stand a chance yet he starts shit talking.

Qing stretched her lips as if she found it laughable.

Hwan Yook couldn't see it because of the veil, but if he did, he would
have been quite wronged.

It was just that he felt like he had seen her somewhere before and asked,
with no other intentions.

"I shall yield the first move."

"How can I accept that? I should be the one to yield to you."

"If you are so insistent."

Qing's place in the hierarchy meant that she wasn't obligated to show
respect to the Nine Sects and One Union.

As such, those who knew Qing's realm were limited to those she had
met in her travels, and those who had never met her would just see her
as a young girl from the Divine Maiden Sect.

Also, the slyness of the former Master who put forth her heart-and-soul
disciple was also a factor. She didn't particularly boast about it, so that
was why Qing was like this, and so was the Shaolin disciple Wolbong.

Without declining, Qing stepped forward lightly.

Master said the sword of Wudang was soft and supple.

I wonder what he's going to show.

Qing lightly scattered her sword.

Third Movement of the Divine Maiden Sword, Butch Heavenly Maiden.

It was a simple diagonal slash stance that Ximen Surin loved the most,
and Qing too had taken to it.

As Hwan Yook met her blade, his arm drew a large vertical circle and his
feet moved in a horizontal arc.

And so, the steel sword he had raised to his right side slid across the
blade in a soft arc and pushed against Qing's stance.

Qing, not resisting the pushing force, spun around to face Hwan Yook.

And thus, they had completed one exchange.

Qing thought.

Ah, so that's how he moves.

They said to look at the eyes to read an attack, and the feet to read
martial arts.

She didn't know much about Taiji Divine Sword, but the one thing that
was clear was the direction of his footwork.

Footwork is to find the most appropriate stance according to the
movements of a stance, thus allowing one to maximize the power of
their weapon.

Namgung Shinjae's footwork was static, not for movement, but to
support his body and keep him standing firm.

Peng Choryeo's footwork was used to continuously rotate his body while
advancing and retreating diagonally, and Peng Daesan's footwork
moved greatly up and down, maximizing the destructive force of his
guandao.

And now, Hwan Yook's footwork was extending out to the left and right,
drawing an arc as if he was drawing a large circle around a distant
point behind Qing.

Two exchanges, three exchanges, four exchanges.

Qing kept pondering.

Is it the angle rather than the distance?

It was a positioning used to guide the flow outwards, and it seemed like
he was rather adding power in the direction of his movement. If she was
caught in that whirlpool, her attack would be reversed to target her
from behind.

Five exchanges, six exchanges, seven exchanges.

It was like a bullfighter's movements.

It was as if he was forcing the opponent to move in a straight line,
moving left and right to pull his body away, and then get on the back of
his opponent.

Then what should I do? Should I attack more swiftly and powerfully and break them in one hit, mix in a trick to guide the circular movement to a blocked path, or should I respond with a spinning movement?

Eight exchanges, nine exchanges, ten exchanges.

As she gently intertwined her sword with his, just as she was responding
to softness with softness, Qing smoothly lifted her right foot.

And in that moment.

She stomped the ground violently with her lifted foot. THUMP!!

The entire tournament venue shook with the impact.

In an instant, Qing's form leaned forward by just one step.

Following that, a sharp sword strike pierced through, aiming right at
her!

Hwan Yook quickly swung his sword to deflect it. CLANG!! The sound
of metal breaking. And at the same time, a shadow suddenly fell upon
Hwan Yook's face.

Hwan Yook's gaze soared. Under the sky of May, it was a beautiful
white hand, covering the sun and casting a shadow.

It sliced through the air and grew ever closer.

The sword was a feint, Hwan Yook belatedly realized, but it was already
too late.

And then… Thud.

Qing's hand blade touched the crown of Hwan Yook's head.