\chapter{The Dragon Ascension Martial Arts Tournament (2)}

When Qing first rose into the arena, the audience was mostly interested
in scanning her body line or wondering what was inside her veil.

But among the Masters, it elicited exclamations of admiration.

It was because it was easy to be brave and fast with their lightness
techniques, but it was extremely difficult to be elegant, graceful, and
demure.

When the leisurely anti-gravity flight of the Yue Maiden Stroll
manifested, those who prided themselves on being Masters all failed
one hundredfold to suppress their exclamations of awe, blurting out
"Hoh!"

Then, when Qing landed lightly on her toes, holding her balance with
not a single sway, it was one thousandfold that they failed to suppress
their admiration. Everyone was busy sending praises like, "How
splendid!"

Except for the Wudang Sect Leader Yu Geukgeom, and the Daoist
Chan Geon, of course.

What a stroke of bad luck, he had met a formidable opponent right
from the very first match of the preliminaries, so wasn't it likely that
Wudang's journey would be cut short?

And then, just when they were about to talk, Qing gently pushed off the
ground first, which was enough to make their stomachs churn.

Because martial artists knew their own realm even if they didn't know
other people's, the Divine Maiden Sect disciple must have said she
would yield the first move, and that Hwan Yuk bastard probably hadn't
recognized his opponent, even giving up the first move himself, so they
didn't even have to listen to know what happened.

And then Yuha Daoist, who was chattering right next to him, made their
stomach churn even more.

"I knew it right away. That child will lead the future of Wulin. That's why
how could I not give her a title? Isn't that right?"

Next to him, Yuha Daoist kept chattering mindlessly. Anyone listening
would think she was a disciple of the Mount Hua Sect instead of the
Divine Maiden Sect.

In fact, he was just flaunting his discernment, so the people listening
looked like they were hoping he would stop soon.

From a Master's perspective, they would praise Qing's amazing
self-control and wit.

It was normal for a young person with outstanding skills to want to show
off their talents, was it not?

But since she was calmly observing her opponent and even imitating
her opponent's techniques, her match wasn't a display of her skills but
a display of her zeal to learn.

And then, what about the single move that had decided the victory at
the end of the tenth exchange?

Having fought with each other's softness, flowing around one another,
she suddenly cut off the circulation by using swift and forceful moves;
even if the Wudang disciple's accomplishments were two or three steps
higher, the result would have been the same.

Moreover, since it was pure improvisation rather than any specific
martial art technique, it was as sharp as a seasoned martial artist who
had been honed in actual combat.

Qing was proud for the same reason.

The vertical stomp was to channel her whole body's strength to create
a downward velocity, and the hand blade strike was just an application
of Ximen Surin's signature killer chop.

It was a bit far from the softness she had intended during her training
in Kaifeng, but she couldn't help but feel proud since she had taken
victory through an action that she had decided on her own, rather than
a technique that was engraved in her head.

Hwan Yuk also accepted the result.

He had done his best and even after reviewing the eleventh exchange,
he realized that there was no way to block it with his current
techniques.

If he had lain down on his Iron Plate Bridge and rolled away, it might
have been different, but since the principle of Wudang's Tai Chi of
receiving the attack and returning it with an attack fell short of that, it
was only natural.

However, people other than the participants and the Masters didn't
understand.

Since it was a fight of soft against soft rather than strong against
strong, the speed at which they exchanged moves wasn't fast.

As such, while Hwan Yuk was moving busily, continuously launching
attacks and displaying the lavish Tai Chi Sword, Qing seemed to be on
the defensive, barely managing to receive his moves.

Since Qing was following along clumsily with the softness, using her
eyes to react, rather than properly using sword techniques, to those
who lacked insight, it looked like she was just showing off her body
without even fighting properly.

Then, in an instant, she delivered a chop with her hand blade,
bonk.

Yes! It was a chop!

And then, the referee immediately blew his whistle, ended the match,
and declared the veiled woman the victor, so the audience was left
speechless with disbelief.

Naturally, the sounds of booing and jeers filled with criticism poured
out into the arena.

Not just criticisms but also trash like half-eaten dumplings and
somyeon (stir-fried noodles) also flew through the air.

Of course, since the audience were not experts in throwing projectiles,
the guests sitting in the expensive front seats had quite a bad time.

-Boo! What the hell is this! What kind of match is this?!

-What is this! Is this a joke of a match?!

-Just because she's a woman, are you showing her special treatment?

-Fight properly! What does gender have to do with a martial arts match?!
You dogshit-

-I bet twenty silver coins on the favorite!

The fact that Qing's odds were extremely low was one of the major
reasons for the criticisms.

Since it was a win-win situation, they had bet large sums on Hwan Yuk,
saying that if they bet on Qing, they'd only win 7\% (1.07x).

Some, who aimed for the underdog, did enjoy a 1170\% (11.7x)
return, but since they were just casual bettors, the small change they
won was merely a bit of pocket money.

For reference, about one-tenth of the betting money that everyone lost
was taken by the betting ticket vendors, and of the remaining money,
about 70\% was pocketed by Cheon Yuhak.

Anyway, for these reasons, the commotion didn't subside, and rather,
the audience, united by their shared disappointment, increased their
criticism.

"Silence!! Be quiet!!"

Even the host's loud voice imbued with Inner Qi couldn't calm the
audience, and it seemed like a riot would start if it were to continue.

In the end, all the way from the arena and down the passage under the
wooden paneling, those jeers were picked up by Qing's superhuman
hearing.

"I am truly sorry that things have turned out like this. It is because the
common people lack the insight to recognize martial arts, so please do
not be angered, Young Lady."

When she returned to the waiting room, a middle-aged martial artist
from the Wulin Alliance spoke to comfort Qing.

"I will quickly ask the elders to provide a commentary on the match, so
it will calm down soon."

To that, Qing shook her head.

She still had more matches in the tournament left, after all.

Afterward, there was the Great Righteousness Assembly? She had heard
that there was an event Master was waiting for.

It would be embarrassing to delay the schedule even further just because
the audience was criticizing them.

And what kind of commentary would they make for such an
embarrassing first match that wasn't even much of a spectacle?

"It's alright. It was just the first match. Once the tournament continues,
those people will realize they didn't recognize my skill. This is
something that will naturally resolve itself, so I cannot possibly trouble
them for my sake, you know?"

"Indeed. I am grateful for your magnanimity, Young Lady."

Yoo Seonyeop, the head of the Wulin Tournament's management
team, and the Dagger Sword General, said with a gesture of admiration
as he gave a respectful fist palm salute.

Not only was she a talented martial artist, but her calm and mature
attitude at such a young age was even more pleasing.

The Alliance Leader had said he would give his Mount Cheon to some
young wench, but now that he faced her directly, she was truly a child
who would grow into a great pillar of the Orthodox Faction in the
future.

Qing didn't know who he was and just thought he was a management
official, but Dagger Sword General Yoo Seonyeop was actually a
housekeeper of the Wulin Alliance who handled all their affairs during
peacetime.

After unknowingly charming Yoo Seonyeop with a Ximen Surin-style
beauty act, Qing returned to the Divine Maiden Sect's seats, where
Ximen Surin was already showing subtle signs of anger.

"Haaa. Perhaps it was because I disliked seeing such a thing that I have
not come out into the world for so long. Disciple, look at this, this is the
perception of the world towards female martial artists. If you were a
man, those bastards wouldn't have dared to speak such ignorant
nonsense."

"Come on, don't worry. Do you think they'll keep saying that after this
disciple wins the tournament?"

"Are you not even angry, Disciple?"

"Not particularly. It's just that those who can't even do a single move are
just shouting nonsense. After all, they'll change their tune at the
tournament finals anyway."

At that, Ximen Surin clicked her tongue.

"Such good guts for a girl."

"Hehe."

"That's not a compliment. What's the point of having such a good heart
when you're a girl?"

Then Qing quietly brought something up.

"But, is there really a need for me to stay here any longer? You said
you're going to that Great Righteousness thing, didn't you, Master?"

"It would be better to watch you since you might face off against
someone. Why, do you have something to do?"

"There is something I need to ask Second Master urgently. Related to
his martial arts."

"Then, it cannot be helped. There isn't any event that you should
participate in anyway. I was going to introduce you at the banquet, but I
guess I'll have to postpone it."

It wasn't about introductions.

Someone like Ximen Surin should have the leaders of the Nine Sects
and One Union and the heads of various families come to offer
greetings, not the other way around.

"Hehe, sorry."

In response, Ximen Surin answered with a smile.

"There is no need for you to be sorry. With your position, there is no
need to make a day just to pay your respects. If you urgently need to
ask something about martial arts, what could be more important than
that?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

For now, she had managed to escape the Kaifeng commandery, but um…

Where should I go now? In this vast land of Kaifeng, finding her master
seemed almost impossible.

But she had heard a voice muttering about selling elixirs, so she
planned to go to the market and start inquiring for suspicious
apothecaries.

But thankfully, there was a voice she heard without having to go far.

"What are you doing? Where are you going?"

"Wow, I was just looking for Master. How did I run into you like this?"

"How did you run into me? I found you after I dipped your Blue Jade
Sword into Chasing Fragrance. How could you have just happened to
run into me?"

"Chasing Fragrance?"

"Slowly now. You have to do the basics first before I can teach you. Don't
be so hasty. So, you were looking for me? Why?"

"It's about this Awakening Divine Art."

"What about it? Isn't it amazing?"

"It's not that, it's just… It's too… how should I put this… yes, that's right,
the stimulation is too strong."

At that, Cheon Yuhak let out a huff of air.

"I was wondering what you were going to say. You're making a fuss over
something trivial. Of course, the stimulation would be intense, as all
your senses have awakened at once."

"Still, shouldn't it be possible to live everyday life? Look here. I can't
possibly walk around all wrapped up like this every day."

Qing rolled up her sleeves, showing the tightly wrapped sleeves.

Cheon Yuhak huffed again.

"You're the type of person to just blunt the edge of a sword because it's
too sharp. Hey, you foolish thing. Would a chef blunt all their blades
because the blade is too scary?"

"What does that mean?"

"When a chef uses a sharp knife, they get cut here and there before
getting better, right? So why did you wrap your awakened body like
that?"

"Well, the stimulation is too-"

"You're so frustrating. Are you going to walk around all wrapped up for
the rest of your life? If that's the case, why even bother awakening your
senses? It might be uncomfortable at first, but you have to gradually
become used to it."

He was just telling her to endure it.

Of course, Cheon Yuhak, who was speaking, hadn't achieved such a
result in a single go with a miraculous elixir. He gradually became
sensitive to senses, step by step, so adapting wasn't too difficult.
Therefore, he didn't even slightly understand Qing's situation, who
had suddenly reached the eighth stage of achievement.

Moreover, he also didn't know about the existence of the Blissful
Maiden Arts.

From Cheon Yuhak's perspective, it seemed like she was just hurting
too much since her skin was chafed because her achievements had
suddenly risen too much.

However, the nature of senses was such that it grew accustomed to
the same stimuli when repeated.

So he was telling her to endure it and become used to it.

"The achievement of your Awakening Divine Art is already at the eighth
stage, and you can't just undo it now. Moreover, do you even know what
it means to have all your senses sharpened? It's as if you have eyes all
around you."

When she completely grasped the skill of reading the air current with
her skin, she would be able to vividly map out a certain radius without
looking at it.

"Wow, really?"

Qing, who was easily swayed, was again hooked on his words and her
eyes sparkled.

Now that she was his disciple, there was no reason for Cheon Yuhak to
exaggerate or hide the disadvantages.

"Well, there is a drawback that you have to be a bit picky with your
clothes."

However, the less air that could low through the clothes, the more
the effect decreased.

If the sleeves and hems of her trousers were tightly bound, blocking the
flow, or if she wore layers of clothes, it was practically pointless.

Conversely, the larger the area of skin exposed to the outside, the
wider the range one could grasp.

Therefore, it was best to wear clothes that allowed airflow, or if not,
one could choose clothes made of silk as thin as gold, which would
react sensitively even to the smallest currents.

"That's why those who specialize in reconnaissance focus on their work
when the cold wind blows. There's no need to go around stealing on
cold days, you know?"

"Hmm. If it's as you say, wouldn't that be a bit embarrassing…?"

To that, Cheon Yuhak nodded.

"Now that I think about it, there are some aspects that are a bit
disadvantageous for women, but it's not like a na sam is embarrassing,
is it? Yes, you can just wear a dan hyung."

A na sam refers to a loosely woven silk, which was nearly
transparent unless one looked at it very closely.

A sa sam was a silk even more loosely woven than that, and a veil was
silk that was even more loosely woven than that.

"Ugh. A dan hyung is a bit…"

Anyway, what Cheon Yuhak was trying to say as her master was clear.

This was the Awakening Divine Art you chose. Endure it.

Though if Qing were to think about it, she didn't exactly choose it.