\chapter{The Hidden Dragon Martial Arts Tournament (1)}

As Cheon Yuhak had said, upon waking up in the morning, one would
come to realize the wonder of feeling the low of the universe.

It was a completely incomprehensible concept for her, but experiencing
it directly was… Ooooh.

The fact that the acute sense that she used to feel only at her fingertips
was expanding to every inch of her skin was the true ability of her
awakened Divine Arts.

When Qing waved her hand, she could clearly feel the air parting
along her skin.

After wandering around the room a few times, she clearly felt what it
meant to feel the flow of the universe with one's body.

She wondered if feeling at one with nature was like this.

Due to Qing making noise as she wandered about, Gongson Yoye seemed
to have woken up.

"Young Lady Ximen……? Are you awake?"

"Yeah. You slept well too? You're going to the opening ceremony,
right?"

"A-About that. One must attend the opening ceremony with their
family, so I am truly sorry, regretful, and apologetic for not being able
to go together, Young Lady Ximen. My heart is truly longing to be
with you too, bu-"

"Ehh. Family comes first. You should go on ahead. I'll eat a light
breakfast and head there slowly."

Qing smiled, assuring Gongson Yoye, who seemed about to break
down, that it was okay before putting on her clothes.

Her swordsmanship training was becoming much more familiar.

After putting on the undergarments that the servants of the
Heavenly Martial Pavilion had prepared, Qing, full of confidence,
carefully put on the Divine Maiden Sect robes while holding her
sword.

Today was a formal event, so she had to wear the Divine Maiden Sect
robes.

She felt in top condition starting from the morning.

Was it because she had consumed too much elixirs yesterday? Her body
felt so light and refreshed. She had not felt this invigorated in such a
long time.

As such, while heading to the dining hall, the soft feel of the silk lining
of her robes brushing against her skin felt exceptionally great.

The softness of the silk brushing against her skin, almost as if to
demonstrate that there was a reason why the word 'silk' existed.

It was akin to the feeling of wrapping oneself in the most comfortable
bedding.

Just strolling around, enjoying that very sensation of rolling around in
bed. Every step was practically heaven……

Hm.

Qing's light strides gradually slowed down.

The arms she had been swinging so vigorously were now cautiously
tucked in at her sides. Suddenly, the demure and graceful gait of the
Ximen Surin kind made its appearance.

It felt good, it truly felt good, but this is all… too… What's a good
word for it? Seductive? It's just walking, but still……

Qing winced behind her veil.

Isn't this a huge problem……

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Forget the Divine Arts Awakening or the martial arts tournament or
whatever, Qing urgently took emergency measures.

Although brushing her body with soft fabric might seem nice at first,
the accumulated stimulation was something that could not be
ignored.

To reduce stimulation, she wrapped her arms and legs with silk sleeves,
and tightly fastened a wide belt to her stomach to hold the clothes
firmly against her body.

During this, she had wasted too much time, arriving at the martial arts
tournament site when Martial Alliance Leader Cho Hyunryang was
already going on and on about the Righteous Faction, and how it was
so righteous, blah blah blah.

Qing looked around furtively before asking a Martial Alliance warrior
for assistance.

She had been told of the general location of the Divine Maiden Sect
seats, but the tournament site was too large and she couldn't find her
seats.

The tournament site was located in the center of Kaifeng, at the Grand
Canal in front of Kaifeng Mansion.

As it was a canal that stretched all over Zhongyuan, connecting to
all three great rivers, the starting point that connected to all waterways
of Zhongyuan was of an appropriately grand scale.

The martial arts tournament venue was created by floating rafts and
connecting them to the floor.

After looking around furtively and pushing her way through the crowd,
and then awkwardly pushing through the seats, Qing was finally able to
ind the Divine Maiden Sect's seat.

"Oh. Teacher. You were already here? Are you participating in the
tournament?"

"Why are you only arriving now? Why can't you get here in time? How
can I feel at ease with you like this?"

"Hehe……."

I'm glad Teacher's here, Qing thought to herself in relief.
Compared to the other sects, who had all come in large groups of
dozens or even scores of people, the Divine Maiden Sect was quite
modest, making her not know what to do all alone. But now, she could
just follow Teacher around.

"You didn't even go visit the Nine Sects and One Union kids to greet them,
just training by yourself, right? Well, I guess it's not an easy task for
you to do that alone."

The 'kids' that Ximen Surin was talking about were the sect leaders or
elders who were attending as proxies.

To Ximen Surin, they were at the level of her disciples, but it was inevitable for Qing
to feel a bit weird about it.

After that was a rather tedious time.

If one was to ask what kind of event a martial arts tournament was, it
would be to strengthen the bonds of the Righteous Faction and display
their power.

In other words, it was a combination of socializing, mental training,
and military displays.

And there were several events for that purpose.

A rally where anyone from the Righteous Faction could speak freely and
respond, a challenge match where one could challenge an Absolute
Master of the Righteous Faction, a great operating council where one
could vote on agenda items selected by the Martial Alliance and help
operate the Righteous Faction of Wulin, and so on.

However, the event that ordinary spectators most looked forward to
was definitely the Hidden Dragon Martial Arts Tournament, a
compelling competition between the rising talents of the Righteous
Faction.

The opening ceremony, however, was difficult to endure.

Starting with the opening address by the Alliance Leader, the martial
arts luminaries would each say a few words. Just one representative
from the nine sects and one from each of the ive noble clans. And then
someone else named so-and-so came out to talk and talk and talk……

However, the spectators were surprisingly enjoying it.

Wow! A Master of the Ten Under Heavens! Wow! The Sect Leader of the
Jongnam Sect!

Just the appearance of the Absolute Masters of Wulin was enough to
excite them, so they would utter things like 'Ooooh, as expected,' 'Hmm,
such a profound meaning' even during the typical congratulatory
speeches.

Qing couldn't understand it, but it was because the culture of
entertainment was very primitive and uncivilized in ancient China.

Unlike her home, where one could see famous people at any time on
the screen, most people had come to Kaifeng, traveling thousands of
miles, just to see the face of a Master of the Ten Under Heavens.

And then, the highlight of the opening ceremony, the lottery for the
Hidden Dragon Martial Arts Tournament, took place.

As the Alliance Leader drew the tickets personally on the stage, the
emcee would announce the names and write them on a large tent.

Qing was bored to death, wondering when they were going to finish the
lottery for more than sixty participants and create the bracket, but
actually, this was the very moment that the spectators had eagerly
awaited.

"Kunlun Sect Disciple Jin Sam! From Tadong, Bae Jaehap!"

The emcee with a great voice announced the contents of the ticket he
drew, and then the spectators would start chatting amongst themselves.

Wouldn't the Kunlun Disciple win in this matchup?

I saw Bae Jaehap in the preliminaries, and he was wielding that staff like
it was an extension of his body.

From what I've seen, I think this is going to be a close matchup.

This was partly out of curiosity and a study of victories and defeats,
and partly a discussion to try and make a score on the gambling
matches.

As Qing was forcibly enduring the boring time, her name was announced
towards the end of the third bracket.

"Divine Maiden Sect Disciple Ximen Qing! Wudang Sect Disciple Hwan
Yook!"

She didn't know who they were anyway. Maybe she had heard their
names at the Hidden Dragon Tournament or something.

More than that, she was curious about the spectators' predictions. As
such, Qing quietly listened to the voices she could hear.

-Without a doubt, that's going to be Master Hwan Yook. When talking
about Wudang, you have to talk about the Taichi Sword, and when
talking about the Taichi Sword, there's no other choice but to say it's
the greatest swordsmanship under Heaven. It's going to be a boring
match.

-The Divine Maiden Sect doesn't have any particularly outstanding
martial arts, though. Do they even know any martial arts?

-We don't know that yet. There's a rumor that Master Yoo Ha of the
Mount Hua Sect highly praised them, you know? This is when you make
a killing by betting on the underdog.

-But you just said you were betting on the underdog……

From what she heard, it seemed that most people were predicting the
Wudang Disciple to win.

Hm. Is he somewhat strong?

If Jegal was here, he would've annotated it for me.

That was when it happened.

"Shaolin Disciple Wolbong! From the Black Dragon Clan, Cho Hakche!"

At that, Ximen Surin voiced her thoughts.

"That bald monk. This must make Cho Hyunryang feel a bit bitter."

"The Alliance Leader, you mean? Hmm. Are the Shaolin disciples that
strong?"

"If the Dharma name is Wolbong, that is a disciple from the same
generation as your own. Who do you think his master would be?"

The current Abbot of Shaolin was Grand Master Wolhyeon, whose
Dharma name began with the character Wol.

If it was Wolbong, that implied that it was someone from the same
generation and a direct disciple of a Master with an even higher
generation.

Since there was only one such figure at Shaolin, it was a direct disciple
of the Greatest Under Heaven, Great Master of Martial Arts.

"How could they keep a disciple of such a level hidden until now……."

"Hmm. Is he a very strong opponent?"

"Shaolin is a sect that would never send out a disciple if they weren't
confident of winning."

The actions of Shaolin were always so heavy and rarely did they make
any moves for trivial matters.

But when they did, it was said that they could move even mountains,
and this was the very weight that the head of the Righteous Faction and
the origin of Orthodox Martial Arts held.

"He will be your opponent in the semi-finals."

Ximen Surin stated as if it was the most obvious thing in the world.

The Hidden Dragon Martial Arts Tournament was composed of four
brackets, and if Qing reached the semi-finals along with Wolbong, who
was in bracket four, then they would be forced to face each other.

"Eyyy. Don't worry too much. Your disciple is the strongest among the
rising talents, after all."

Ximen Surin responded with a smile.

"You don't need to feel pressured. If you were to lose to a Shaolin
Disciple, no one in the world would think it strange. But."

Ximen Surin's eyes gleamed.

"If possible, I wish for my disciple to show the world that you can
defeat a Shaolin Disciple."

At that, Qing was about to thump her chest, but stopped and clenched
her ist tightly instead.

"Of course. You can depend on me."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A martial arts tournament was a place where all the Masters of the
Righteous Faction were gathered together.

Therefore, anyone with a functioning mind would never even think of
causing trouble in a martial arts tournament.

That is, if they had a functioning mind.

And in the world of Wulin, there were quite a few individuals who
weren't right in the head. And among them was a group with an
ominous name, called the Blood Cult.

In fact, the very fact that they called themselves the Blood Cult was
proof that they weren't right in the head.

Even the Unorthodox Faction did not call themselves the Unorthodox
Faction, but used the term Deviant Path. Even the Demonic Cult
referred to themselves as the Heavenly Demon Divine Cult or simply
the Divine Cult.

It was for this very reason that the Blood Cult was so infamous in the
Zhongyuan.

Even though the Demonic Cult was infamous, they were like
barbarians who periodically invaded Zhongyuan, shouting that
they would conquer the world.

But what about the Blood Cult?

The only goal of those bastards was to bring a bloodbath to the Central
Plains, so it was not at all strange for them to do anything. They were
the true crazies.

Therefore, the members of the Blood Cult were lunatics that could
suddenly appear anywhere at any time.

And thus, a lunatic from the Blood Cult had infiltrated Kaifeng, where a
martial arts tournament was being held.

He was a Demonic Adept known throughout Jianghu as the Mad Demon
of the Despised Path.