\chapter{The Hidden Dragon Martial Arts Tournament (7)}

"The winner, Divine Maiden Sect disciple, Ximen Qing!"

In response, the audience once again erupted into boos.

Qing snickered once again under the veil.

It seemed my odds were quite high this time around too.

I don't have some kind of a chosen one complex or anything, but it was
absolutely impossible for ordinary civilians with their limited view of
the world to comprehend my martial prowess.

It was indeed so.

Qing hadn't showed anything in the previous match and since the
unaffiliated martial artists had shown a revolutionary leap in skill, her
odds were once again high.

Of course, they weren't as high as before, so there were some who
made a profit by betting on Qing, but the contents of the match felt
rather lacking.

The only time the blades clashed was just once and unlike the menacing
attack of Doryeoman, which was almost unbelievable to see in action,
Qing was busy acting all graceful and elegant, mostly focused on
defense.

Then, just as Doryeoman suddenly rushed forward with his blade, he
had given her the win.

Of course, when coincidences keep on happening, one had to suspect
that it wasn't a coincidence at all and wonder if the Masked Sword
Woman was truly talented.

However, whether it was in Zhongyuan or the West, whether it
was this barbaric medieval world or modern times that claimed they
were not barbaric, there was no particular need for reason when
denouncing an ugly person.

Someone just had to be the first to boo, those who lost money would
respond to it, and the rest would just think, oh I see, well, that ugly
bitch probably had used some tricks.

While the announcer tried to get the crowd to calm down, Qing jumped
down from the arena's passage.

Then she looked back and forth once, before sprinting away using her
Thousand-Mile Flight technique.

"Young Expert Do! May I have a moment of your time?"

"Hmph. Young Lady Ximen."

Doryeoman, who was returning to his waiting room on the opposite
side, clasped his hands upon seeing Qing. He seemed uncomfortable as
he glanced around and then spoke.

"I must apologize that despite the generosity of Young Lady, public
opinion was not all too welcoming."

"It is not up to Young Expert Do to feel sorry, wouldn't you agree? There
are still more matches, so those people will come to acknowledge this
one's true strength sooner or later."

"How kind your heart is. Huh. It is not that I had any other intentions or
-"

"Oh no, are you about to feel apologetic again? It's fine." Qing shook
her head dismissively.

And then, she brought up the main reason she grabbed onto Doryeoman.

"I do not know much about martial arts, but it does not seem that
Young Expert Do's Single Yang Blade is a martial art built upon
extreme swiftness. Am I correct?"

"Yes, in fact, that is so. But, how were you able to tell that……"

"Well, the thing is."

Having said that, Qing found herself at a dead end.

For now, I managed to grab him since he felt so suspicious, but what
should I even do now?

I can't just ask him what he had been up to that was worthy of
obtaining such a high amount of Evil Karma, nor could I indirectly ask
him if he had been up to no good or something.

If his score was over 100, I might have even given him a beating, but he
was four points short, which was rather irritating.

It was then.

"Ugh……!"

Doryeoman's back bent like a sickle as he retched, letting out an
unpleasant noise.

Fortunately, other than the long string of saliva, there weren't any of
those semi-solid and semi-liquid mixtures, so it was just a rather severe
case of dry heaving.

"Young Expert Do. Are you alright?"

"Guh, it's, it's okay, Ugh."

But no matter how you looked at him, he looked far from alright.

Qing gently patted Doryeoman's back.

Should I take him to a doctor?

But it wouldn't be right to just leave him like this.

"I'm alright now……."

"Are you ill anywhere? Perhaps you have some kind of chronic
illness."

"No, it is just."

And then he paused, glancing at Qing carefully before sighing and
asking.

"Young Lady Ximen. What would the difference between an elixir and
something that isn't, even be?"

Huh, why are you asking me?

"Well. I wouldn't know."

"To be honest, I had the fortune to meet the Divine Thief."

"Ooh."

Qing's eyes became round.

Of course, her expression was hidden by the veil, but anyone would
just start laughing upon hearing the unique noise she made.

"Haha, Young Lady, you have quite an unexpectedly cute side to you.
Ah! Please do not misunderstand, I just had a more… perhaps, elegant
impression of you."

"To be fair, I was acting all elegant, you know? Seems like it had an
effect on you. So, you met the Divine Thief?"

"Yes. And the Divine Thief gave me this pill."

With that, he pulled out a wooden box from his bosom and revealed two
crimson pills.

Hmm. The color is a bit odd, though. It seems really sketchy at a glance.

"It's called Jamsamdan. Do you, perhaps, know about it?"

"Nope. Is it famous?"

"It is a pill that grants the user an overflowing amount of True Origin
energy for a short amount of time."

"True Origin Qi? If it overflows, won't your life span……"

"Indeed. It is a pill that lets one transcend their limits for a short time at
the cost of one's life span. However, since the user draws upon their
True Origin, it is incredibly harmful to the body, thus why I'm like
this."

"Ah……."

To say it according to Qing's hometown's terminology, it was a doping
drug with doping side effects.

But, was it actually doping? If someone uses their own lifespan
willingly, is it something evil? Do you just get an Evil Karma boost or
what?

Since this was Qing's first time at a Tournament, she did not know the
rules of Zhongyuan.

Is this illegal? Is it evil? Seeing as he just told me so frankly…

"Perhaps you are disappointed?"

"Hmm. I don't really know. Is it something I should be disappointed
about? Besides, isn't it unrelated to us?"

If this was her hometown, the modern world, Qing would have been
able to denounce it as doping.

However, this was Zhongyuan.

One could walk with pride under heaven as long as their Inner Qi was
enhanced with elixirs, but using a pill that temporarily drew upon one's
True Origin would be considered a cheap trick or fraud?

Doryeoman just blankly stared at Qing.

"Young Lady does not seem to be a martial artist from a famous sect.
Ah, please don't misunderstand my meaning and-"

"No, it's okay. Before my teacher took me in, I was a wandering ronin. It
hasn't been that long ago. Probably only about four years ago."

"Ah, I see."

Doryeoman smiled, then grabbed one of the pills and wrapped it in a
handkerchief before placing it in his bosom and then offered the wooden
box to Qing.

"I shall give this to Young Lady. However, please do not use it at the
Tournament. You will probably be denounced for cheating."

At that, Qing understood the trend of the unaffiliated martial artists.
All those unaffiliated martial artists must have been participating
after taking drugs, huh. I knew my  Evil Karma had suddenly
increased.

But is that considered a sin?

Isn't the status window being a little too stingy?

Aside from that, why give it to me?

"But why me?"

"It's what they call a life-saving talisman. If you take it during an
emergency or before a life-and-death battle, it will clearly be of great
help."

"Ah. That's right."

As this was a Tournament, she hadn't thought about that.

Indeed, it would be better to shave a bit off of her lifespan than to
actually lose her life.

"Then, isn't it valuable?"

"I also received it without paying any particular price. The Divine Thief
gave it to me as something good to have, saying he wouldn't mind me
stealing victory one time."

You wanted to sell elixirs but now, you're selling this crap?

But why?

If I'm curious, I can just ask.

After all, she wasn't exactly a stranger to the Divine Thief.

If she had to put it into words, she was currently carrying on the
heritage of the Divine Thief, you see.

It was a rather terrifying way of putting things, but it was indeed a fact.

Then, I don't really have to accept this pill. I can just get it from
Teacher, you know?

However, she wasn't able to reject it before it was already being
handed to her.

"Then. Farewell."

"Ah, yes. Please be on your way."

Doryeoman gave a courteous bow as he departed.

His back looked truly carefree.

And in the meantime, her Evil Karma, huh?

What? Why has it decreased by 50 points? Was it for revealing the fact
that they had doped? Does that reduce it by 50? Or was it for handing a
pill over to me? Did that reduce it by 50 points?

Evil Karma piled up like nothing but accumulating Righteous Karma was
truly difficult, with strict rulings.

It only amounted to a fraction of one point of Evil Karma even after
slaying a villain, so accumulating 50 points would mean slaying over
5000 points worth of Evil Karma.

Just what the hell was going on?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since her match was over, Qing left the tournament's arena, headed to
a rather secluded corner of the city, and began to eat some snacks.

While she was doing so, Cheon Yahoo quietly sat on a chair opposite
to her.

"Ah. Teacher has arrived."

"Of course. Am I not here because you wanted to see me?"

With some mystical technique called Scent Tracking, Cheon Yuhaok
could somehow find her disciple no matter how far she was, so naturally
she thought he would come.

And naturally, he had appeared.

"You're right. Ah. That's right. About that elixir you said you were
selling-"

"Ahem, cough, cough. Who said something like that?"

"You can try to deny it, but I've already caught you, you know? Someone
told me that they had bought one. Here."

Qing handed over the wooden box to him.

Cheon Yuhaok opened the wooden box and tilted his head.

"What? Is this an elixir?"

"It's called Jamsamdan. They said you gave it to them."

"Ah. Jamsamdan. Right. I had some of those made by that Divine
Physician, but I forgot to give you one. I will give it to you later. But
wait, what? Who gave it to you?"

As Cheon Yuhaok was still pretending he didn't know anything, Qing
explained Doryeoman's story as it was.

At that, Cheon Yuhaok's expression turned serious.

"That's odd. I never gave them anything. What kind of bastard dares to
impersonate me? What? To steal a victory?"

"That sounds just like you, though? It actually seemed plausible."

"Well, it does sound fun, but it wasn't me. Hmm. Why didn't I think of
that?"

Cheon Yuhaok cut her off as he said that, then paused to organize his
thoughts.

"I hear that you're close to that Tang Clan woman. Ask her once. Tell
her to find out whether the drugs given using the Divine Thief's name
are the real deal. I'll have to check on that."

"And what will you do after you've checked?"

"If it's the real deal, I will just leave it alone. If the drug distributed
using the Divine Thief's name is strange, I have to retrieve it. What do
you think, you brat? Are you going to treat this as someone else's
problem? This is a matter of the Divine Thief's reputation."

"Hehe………"

With nothing to say, Qing brushed it off with a coy chuckle and brought
up another topic.

"Ah. Teacher. What about the Meridian Reversal Torture method? Can
you perhaps do it for me tomorrow?"

"Torture method? Well, it's not entirely incorrect. But there are still a
few days left before your rest, aren't there?"

"I think I should do it as close as possible to the next match to
prepare myself. And my body is in peak condition too."

"Aigo. Just because you say you're okay doesn't mean we can do it right
away. I'll have to stay up all night to prepare. I am really suffering
because of you disciple, y'know? But is it truly okay? It feels like your
eyes are trembling a bit already."

"Wouldn't it hurt less because of the Awakening Technique?"

At that, Cheon Yuhaok snorted dismissively.

"The sensation of the skin has awakened, but has the sensation of your
joints and tendons awakened? The pain will still be the same."

"Couldn't you say something like how it'll hurt less, just as a gesture or
something?"

"If I deceive you with lies, I will only incur your resentment later. Well,
seeing how you're the one asking to do it first, I guess it means you have
some kind of nefarious plan in your heart."

If I wanted to train, I could not avoid the pain. Moreover, even when
my body was perfectly ine, I couldn't just idly put it off while trembling
in fear.

After all, wasn't training the very action of overcoming pain and
becoming stronger? The people in Qing's hometown who exercised
were the same.

The pain only became the problem when it was too much, excessively
so, to the level of resembling an atrocious torture.

Besides, it was such a tedious task that even Cheon Yuhaok became
exhausted. So, it was not as if her disciple could just skip it because she
didn't want to feel pain.

More than anything, how would a teacher's heart feel if they were
going to give it all, only for her to avoid it because it hurt?

So, it was best to make a fuss about it and get it over with as quickly
as possible.

That was Qing's judgment.

She also had some sense of confidence.

After all, wasn't this the same body that had brilliantly adapted to the
pain of having her skin ripped off over the last five days?

It meant she had somewhat become accustomed to this thing called pain.