\chapter{The Hidden Dragon Martial Arts Tournament (8)}

"Ah, Nanah. I picked this up on my way here. Can you take a look at
what it is? They say it's a Jamram Pill."

"Huh? A Jamram Pill? You shouldn't pick those things up so recklessly.
Their side effects and effects can vary wildly."

Cheap Jamram Pills had barely any effect and yet consumed Inner

Force, making them practically no different from a suicidal poison.

On the other hand, well-known top-grade Jamram Pills had an
explosive power that could be extracted in an instant, or had almost
no damage to one's Inner Force, or both, or whatnot.

Tang Nanah, who became strict when it came to any harmful
substance, was about to launch into a long lecture, but she frowned
deeply upon opening the wooden box.

"What the hell, it's all crimson?"

"Is it bad if it's red?"

"You can create colors, of course. There's Korean angelica, saflower,
and wolfberries. But it's rare to make it red. Normally, if a pill is red, you'd
try to erase that color, making it pitch black. Otherwise it'll feel
unsettling……"

Upon hearing that, it seemed that was true.

The pills given by Doreman were a blood-red color, causing an
aversion that felt chilly just by looking at them.

"Hmm. Then, can you tell if it's a good item or not, and what the side
effects are?"

"Hmm. Is this something that I have to examine secretly? Can't you ask
the elders of the clan?"

"Uhm."

Qing pondered for a moment.

Since it was something with the name of the Divine Thief attached to it,
it seemed that things would get complicated even if it was a low-grade
item.

How wronged would Teacher be if the rumor that the Divine Thief had
spread a poisonous elixir was to spread?

"Yeah. I would like you to do it secretly."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The next day.

Qing, whose body was swollen due to absorbing the pill's power, was
tightly bound to the torture bed.

The fear was slowly beginning to rise once again.

Once her joints were tightly fixated with iron shackles, she truly
couldn't move a single finger.

It felt like she was standing on top of a free-fall ride in her hometown.

Why did I even say I would do it with such confidence?

I shouldn't have done it.

Is it too late to just get it over with and go down now?

In the meantime, Cheon Yoohak was dragging some ropes over, tying
Qing and the training bed together.

"Teacher? You didn't do this before."

"After the last one, I inspected the training bed and found the shackles'
joints to be loose. I'm no expert in steelworking, so if they break, there's
no way to fix them. That's why I have to prevent them from breaking in
this way."

He could do some maintenance, but he didn't have the ability to ix
them if they broke.

If they broke, he'd have to hand it over to the ironworks, and who knew
how long that would take. It would push back the Yuryu Yeonryeon
Training even further.

As such, he was going to reinforce it with other means.

"In the first place, what kind of girl has so much strength?"

"Agh, could you please do it a bit more gently? It's too tight. And it's
really painful, what is this?"

"It is a Divine Weapon called the Dragon Bind. Once the swelling
subsides, it'll be a perfect it, so just endure for about two and a half
shichen."

"The torture lasts three shichen, but you're telling me to endure two
and a half?"

"Once it starts, you won't even notice how tight it is anyway. Well, let's
see. Huff."

And then, the ropes were not just one spool.

They were tightly bound on both arms. Tightly on both legs. Thickly
wound around her stomach and even tightly around her neck.

They weren't just ordinary ropes, but a kind of weapon with a name,
increasing Qing's knowledge that she really didn't want to know.

They were rope-type weapons called Seunggneung or Sak.

"Teacher, my breath, I can't, I can't breathe. Is it, is it too tight around
my neck?"

"It's because your belly is too tight. There isn't enough space for air to
enter your chest, but I suppose you'll be alright for about three shichen.
Probably."

"Probably, my ass, that's-a-gibb-erish."

Even if one has a body that transcended humans, if their mouth is
gagged, they couldn't form words.

Qing tried to protest by wriggling, but she had been tied so tightly that
there was no room for her lungs to expand within her chest cavity.

As such, she could not move even a single hair.

Rather, the more she tried to struggle, the more her lungs deflated and
expelled the air left inside.

Then, as her tightly bound belly could not expand, her lungs were
unable to perform their function.

I can't, I can't breathe……!

It was just when Qing was desperately trying to take a breath.

The training bed bent in the opposite direction of her joints, and at the
same time, all of her joints from her fingers to her shoulders were bent
outward, causing that surge of pain-

Qing saw the familiar ceiling.

It was the single room that she had not seen in a long time, the place
where the blue-collar worker had lived before her debut into Wulin.

That's right, it used to look like this.

I haven't thought about it recently, so I had forgotten.

Then Qing tilted her head.

But why am I here?

Qing searched her memories and at the same time, a rush of terrible
pain came flooding back-

"Ah. That's right. I passed out."

Qing realized her condition.

Since it hurt so much she wished she could just die, she must have
passed out for a moment.

At that moment.

An alien voice was suddenly heard.

-HIIIIIIEEK! HUUUUUH, HUUUUUUH, HUAAAAAH!

When Qing turned her head, she saw a muscular, long-haired man
who was screaming in shock in her single room, despite having
trespassed into her home.

-HUAAAAH! HUAAAAH……!

It was the spirit body of the former Heavenly Demon.

Huh? What is with the mental parasite?

He was writhing, trembling in fear when seeing Qing, his eyes were
vacant and he was no longer producing any kind of human sound.

"What, why is he like that? Hey?"

-KYAAAAAAAH!

The former Heavenly Demon shrieked like a girl and buried his head into
the floor, covering his ears.

It was said that ostriches buried their heads into the ground when
faced with a natural enemy. They seemed to believe that if they could
not see their enemy, their enemy would not see them.

It was unknown whether it was a parable or a true fact, but the former
Heavenly Demon's spirit was acting exactly like that.

What's happening? Why has he become a complete moron?

Surprisingly, the culprit was Qing!

The human unconscious did not tolerate intruders who could steal
their physical body.

That was the reason why Qing's unconscious kept breaking the Heavenly
Demon Spirit like popping bubble wrap in every moment that she was
asleep.

The pain of his spirit being shattered had exceeded tens of thousands
of times, causing his mind to collapse completely.

But Qing did not know this.

If she could have known, it would not have been called the
unconscious, but the conscious. As such, not even the grand master of
psychoanalysis, Master Freud, and his disciple, and also rival, Master
Jung could have known about this.

Then, suddenly, Qing's senses rang an alarm. It was a signal that she
was about to wake up.

"Ah, this isn't good……!"

Qing's expression changed to the same one as the Heavenly Demon,
who had buried his head on the floor.

Please, let me remain passed out a bit longer. I hate pain. I was wrong
about everything. Please, please…!

Then, suddenly an idea came to her mind. Hmm? Wait a minute?

SHLASH!

Ice-cold water slapped Qing's face. If you were to ask why there was
cold water in late May, it would have to be said that a chunk of ice she
bought from the ice shop also slapped her on the face at the same
time.

"Uuuuuh! Uuuuuuuh!"

Upon regaining her consciousness, Qing let out a suppressed sound
from beyond the gag.

Based on his own experience, Cheon Yoohak roughly guessed it was a
string of curses. After all, Cheon Yoohak had also spewed countless
curses while he was gagged during the Yuryu Yeonryeon Training.

But?

Cheon Yoohak's narrow eyes narrowed even further.

Is it just my imagination……?

However, he had no time to let his mind wander.

Yuryu Yeonryeon was a high-intensity physical and mental labor not
only for the one being trained, but also the one in charge of training.
Cheon Yoohak adjusted the device again, focusing on the subtle
sensations that reached him.

Ah. Should've done this earlier. Ah, how comfortable.

Qing lay down on the bed and looked at the screen.

Her eyes were shaking so much that she could not recognize the place
that was projected on the screen, even though it was obviously the
ceiling of the bath. Her pupils were shaking so violently they were
going in all directions.

Of course, it wasn't like Qing was just playing around.

"Not a chance."

The moment Qing focused on her dantian and cut off the Heavenly
Demon Spirit's will, the Heaven-Shattering Demonic Qi that had been
about to surge up calmly returned to her dantian.

When I try to control this demonic energy, it hardly moves an inch, but
when that mental parasite takes hold of my body, it goes absolutely
wild!

However, even when the Heavenly Demon Spirit was whole, it could not
be a match for Qing mentally.

Much less now that it was a complete moron.

As such, even if Qing were to die, there was no longer a need to worry
about the Heavenly Demon's second coming.

The Heavenly Demon Spirit might be immortal, but the collapsed
mind was no longer capable of taking over even a weak child's body.

As such, Qing observed the painful sight of her body being torn apart
on the screen as if it was another person's matter.

Rather, it was a tough time because it was too boring.

But that didn't mean she could just completely let go of her mind; she
had to suppress the Demonic Qi of her dantian that was trying to run
wild by focusing.

How much time had passed?

Upon seeing Cheon Yoohak's sparse hair appear on the screen as he
removed her gag, Qing shoved the mental parasite into the deepest
depths of her mind.

Even though she only let her body be controlled for about two and a
half shichen, the weight of her torso felt like lead and her joints ached
all over.

Still, since the pill's effect had worn off, the swelling had also subsided,
thus allowing her lungs to breathe comfortably.

Since everything that Cheon Yoohak said about three shichen was
correct, she also felt wronged for some reason.

"Aigo, I'm going to die……"

Cheon Yoohak, who had spent three shichen using his full strength to
maintain a hyper-focused state, collapsed immediately as before.
Qing shouted urgently.

"Teacher!? Could you please! Loosen me! Before! Resting! Please!?"

"Later, let's do it later…… You're tired too, so you can't move anyway."

Since people gave strength in pain, Qing's condition was also such that
the muscles of her whole body were exhausted and stretched out, even
though she was bound.

"Still, it would be better if I was in a more comfortable state……"

"Was it only you who had trouble? It's much harder to untie all these
ropes. Just… yeah. Let's just all get some sleep and we'll see."

"Teacher!? I have to go to the restroom! I have to go do number 1! Quick!"

"It's a bath, you know? Just do it…"

Cheon Yoohak, who was about to pass out, said those words and passed
out right after.

Zzzzz. The sound of snoring was deafening.

"Agh, that doesn't even make sense. Teacher? Teacher? Hey! Untie this!"

And then, only Qing's desperate voice echoed throughout the bath.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the end, Qing, who had not been able to sleep at all while Cheon
Yoohak was passed out, barely managed to drag herself to the
Heavenly Martial Pavilion.

And then, as soon as Tang Nanah, who was pacing in the hallway,
discovered Qing, she rushed over.

"Qing'ah, where did you pick this up?! You weren't involved with
anything because of this, were you?! Tell me it's not true! Please!"

"Why? What's wrong with it?"

Qing answered in a hoarse voice.

However, her tiredness was accompanied by a sense of peace.

At that, Tang Nanah was relieved.

And then, she began to speak.

"Wrong, you say? It's an abhorrent and evil weapon made with blood
essence. It's a pill made by melting people down. Where did you pick up
such a terrible thing?"

The easiest way to make a Jamram Pill was to use like-for-like.

In other words, it was a way of awakening Inner Force with Inner Force.

Jamram Pills that used blood essence not only had an outstanding
effect but also caused barely any burden to the user.

If we were to talk about blood essence, then it was a terrible method of
melting a person's Inner Force into a medicine, a product of the Daoist
Alchemists of the Zhou Dynasty.

After the fall of the Zhou Dynasty, the records were burned and the
Alchemists were executed to eradicate their lineage, but the evil ways,
as was often the case, still managed to survive tenaciously and maintain
their lineage.

And there was a power in Jianghu that used blood essence as if it was
only natural to do so; those bastards called the Blood Cult.