\chapter{The Waves in Front of the Yangtze River Are Like This and That (10)}

The strength of the Great Demonic Adept, who had been absolutely shat on, was truly transcendent. To exaggerate a bit, it made the heavens tremble and the earth shake. 

In fact, even the number of five Jiangshis were dangerously close to being insufficient.

The Demonic Cannibal consumed his energy without reservation.

A Heavenly Jiangshi was flung away, bouncing on the ground and skidding away.

No matter how sturdy a Heavenly Jiangshi was, because it was made from a child's body, it could not escape the constraints of mass.

Qing felt as if her heart was being squeezed.

\textit{No, like that fat pig is more than terrifying enough. But what the fuck is up with those kids who can endure that beatdown with just their bodies?}

There would come a time when she had to settle things with this batshit insane, obsessive maniac of a Final Boss.

By then, those shields would also stand against Qing as enemies.

{\itshape As long as this matter goes well, I might be able to shake off that persistent end-stage boss for a while.

In that time, I'll have no choice but to gather Practice Points or whatever the fuck I need to quickly elevate my realm.

For now, let's shit on this guy some more.}

"Do you perhaps know about this? Your manners are absolutely fucked in the ass. Did you eat those too? Even the fucking beggars would be more polite than you."

Qing circled around the Cannibal, continuously provoking him.

"Oh my. If you meet an adult, you should greet them properly, you know? Look, I am a great elder of Wulin. How dare a brat like you, who has fewer days to live than me, treat your betters like this? The audacity."

"YOU BITCH! THAT MOUTH OF YOURS!"

"Oho? What a bad child. Do you not realize the customs of Wulin are strict? Can you not differentiate between superiors and inferiors?! Its because of wild brats like you that there are such distinctions, are there not?"

"This damned! Jiangshi! If not for these things!"

"Anyway, my status allocation is higher than yours. Do you know who my master is?"

In that moment, the Demonic Cannibals eyes sparkled.

This was a chance to find out about this crazy bitch's sect.

The Association would make sure they pay for this humiliation!

Qing smiled slightly.

"Not. Tel. Ling. Se. Cret."

"KEUAAAAAAAAGH!!!"

The Demonic Cannibal tore at his own hair.

Clumps of it fell and fluttered away.

\textit{Hm, looks like he's been marinated nicely.}

Qing started to get to the main point.

"By the way, did you do something wrong to Ah-Ling?"

"...What?"

"Did she really have to go this far-"

For a moment, the Demonic Cannibals movements stopped.

"You bitch, what did you just-"

"What. Why? Suddenly want to talk? Come at me, Fatty. I'm just playing tricks because I'm at such a disadvantage. If you're not gonna come, I'm just gonna leave, okay?"

Qing charged, her arms leading her forward.

It was quite unbecoming of someone who had been dodging this entire time. After all, she swings her arms in a very aggressive manner. When she did so, twenty shadows of arms rushed towards the Cannibal.

Even though hands were clashing with each other, only the noisy sound of metal being struck could be heard.

The Demonic Cannibal kept stepping back.

Sound Transmission was a difficult technique and because it required concentration, he couldn't properly counter.

-You bitch, are you planning to betray the Association!

Suspicion and anger engulfed the Cannibal, causing him to draw delusional conclusions in his mind.

To be fair though, it was a situation ripe for misunderstanding.

-What are you suddenly saying?

-If it is not that, you are probably trying to eliminate me!

-What in the world does that mean. Even if you say indecipherable things.

-If that's not the case, kill this bitch right now!

Yun Yuanling frowned.

Why is this stupid Demonic Adept acting like this all of a sudden?

-Haa. I have already told you. Because of personal reasons, Lady Ximen...

-Shut up! Do you think I will be fooled?!

The Demonic Adept jumped back to create distance and shouted.

"Bu Xiayun, you dullard! You have your son's archenemy right beside you yet you don't even recognize it!"

-Demonic Cannibal!

The Cannibal ignored the protest heard through Sound Transmission. 

"...What is that supposed to mean?"

"I am talking about Yun Yuanling, the bitch beside you! Do you think it is common to find someone who can create such sophisticated Jiangshi in the world?!"

"Even if you are a Senior, please be careful with your words. Young Lady Yun is my son's benefact-"

"That is why I say you are dull!"

The Demonic Cannibal laughed mockingly at Bu Xiayun.

"Kekeke, your son has been long dead, already having stepped on the path to the afterlife. Yet, you think a demon wearing his skin is your actual son. Truly, there is no greater retard!"

"Even if you are a Senior of the Unorthodox Facti-"

"His enemy is right beside you! Can you not see?!"

The shout of the Demonic Cannibal carried such a wrenching sense of chagrin, causing him to draw his attention to a different direction.

"Young Lady Yun?"

Yun Yuanling took a step back and shook her head.

"It is such baseless slander. Could it be that you are doubting the Chief Enforcer of the Wulin Alliance?"

"Do not be fooled! We are the ones to push that bitch into the Alliance!"

"To think a mere Demonic Adept would dare to insult the Wulin Alliance."

"Since we showed you the Blood Jiangshi, we knew you would immediately go find the Yun Clan. Did you think it would be hard to deceive such stupid bastards of the Orthodox Faction!"

"The opponent is a disgusting Demonic Adept. Things like lying are-"

"No, that bitch is the one who is truly disgusting. In fact, she is unrivaled in such an aspect."

The Demonic Cannibal snickered.

"She's the bitch who massacred her entire clan and turned them into Jiangshis, you see."

Yun Yuanling pleaded with a desperate look.

"You must not be deceived by such lies."

"Bring a physician immediately to check on your son's pulse! We'll see if that thing is truly a person or a Jiangshi!"

"Young Master Bu has just recovered. If you check his pulse now, obviously..."

"Bu Xiayun! In your life, have you ever heard of Jiangshi turning back into a human?! "

Bu Xiayun groaned in anguish.

It was because the last words of the Demonic Cannibal had chillingly pierced right through him, digging deep into his heart.

Bu Xiayun made his decision.

"If Young Lady Un is indeed innocent, I am sure she wont resist being taken aside for a while. Would you?"

"Wait, Great Expert! This is what he is aiming for. Without me, how do you expect to deal with the Living Jiangshis?"

Jiangshi. Bu Xiayuns expression hardened.

However, he did not revoke his decision.

"If, by any miniscule chance, the Young Lady is an enemy spy controlling the Jiangshi, it would actually be less harmful for the Champions of the Waterway Forts to deal with the Jiangshi themselves."

"Great Expert!"

"...Take Young Lady Yun away."

"Great Expert, you must not do this!"

Yun Yuanling was dragged away.

Qing watched this scene with extreme anxiety.

After all, that was a true monster, incomparable even to the likes of the Demonic Cannibal.

Qing wondered if she might just explode and kill everyone here.

Fortunately, even though she looked as if she was wronged, Yun Yuanling was taken away without much resistance.

{\itshape They're going to uncover her identity when they investigate anyway.

I wish she would just go away like that.}

Now, the only obstacle left was the Demonic Cannibal.

If she just pushed on like before...

"Look here, Bu Xiayun. I will make you an offer. If you make that bitch kneel before me, I will quietly withdraw. My subordinates as well."

\textit{Ehhh? This was unexpected.}

Qing clenched and unclenched her fist, gauging the situation.

Given that there wasn't an immediate rejection, she had to assume she was already fucked in the ass.

And she knew what those fucking river bandits were like from experience.

Qing gritted her teeth.

{\itshape I still needed to deplete a bit more of his True Qi, though.

I guess theres no other choice then.}

"Stop trying to play dirty fucking trick!"

Qing charged at the Cannibal once again.

The Demonic Cannibal's Flame Demonic Arts filled her field of vision with red hues.

It was right at the moment when the four Heavenly Jiangshis were flung away in her stead.

Qing slipped through that gap.

The Cannibal's arm stretched out towards her heart.

Qing ducked as if to kneel.

The palm wrapped in Qi Force whisked just a papers width above her head. 

Qings figure slid forward while still on her knees.

While recalling a conversation with her teacher, Qing extended her hand.

'Huff, huff, huff. Master. If all I do is dodge, huff, I'll tire out first and collapse.'

'That is only natural, is it not? Making the enemy tire to the point of collapse is the essence of a battle of attrition, as well as a valid strategy.'

'Then, huffff, what if I have to face an Ultra-Supreme Master alone?'

'What in the world is with that term? How could you say something like Ultra-Supreme Master?'

'AH!'

'How can a maiden talk like such a childish ruffian? Tsk, tsk. To face a Master with a high realm alone, you must prepare a trump card. I am referring to poison, hidden weapons, or some strange secret technique that one cannot possibly expect. Seeing how Disciple has an overwhelming amount of True Qi, if you wish to prepare a trump card, an Internal Explosive Qi Strike would be suitable.'

Internal Explosive Qi Strike.

A skill that struck directly at the enemys internal organs with Inner Qi.

A method of brutally forcing ones inner force into the opponent.

There were specialized martial arts for handling such subtleties.

Qings palm touched the Demonic Cannibal's thigh.

\textbf{Tatagatha's Divine Palm. Sixth Movement.}

\textbf{Cintāmaṇicakra.}

Qing resolved herself, thus letting True Qi flow.

The solemnity of the Dark Lady of the Nine Heavens, the purification of Yan Emperor Shennong, the elegance of his daughter Yaoji, and the sagacious True Qi of the Daoist lineage interwove, singing the teachings of Buddhism.

Dinggg!

The sound of a bell enveloped the entire world.

In Buddhism, the bell represented purity.

Purity meant being completely absent of filthiness, free of even a speck of dust.

It signified being clean and untainted by earthly desires, anguish, and passion.

Therefore, the sound of the bell was pure.

It was a sound that was grand yet not noisy.

It was a teaching that was majestic yet not overwhelming.

It was a resonance that was heard not with the ears but with the body, for it was the clearest yet also the heaviest.

The Demonic Cannibal's entire body bulged out.

For a moment, it swelled explosively.

It took the shape of a huge sphere.

One that seemed like it would burst at any moment.

However, soon after, the balloon shriveled.

The shriveled form became the Demonic Cannibal once again and he collapsed powerlessly on the ground.

A giant crater appeared on the ground where the corpse of the Demonic Cannibal lay.

And from that giant crater, dozens of long furrows extended outwards.

It was as if six giant palms had simultaneously pressed down on one point.

Perhaps this was what the handprint of Cintamanicakra, who was said to have six arms, would actually look like.

Only a heavy silence lingered over this land.

A powerful Demonic Adept, who had reached the Late-Stage Transcendent Realm, met the end of his fate.

Moreover, his opponent was a young woman whose name was not even renowned yet.

It was an unbelievable sight to see.

And then, someone broke that silence.

"Really."

It was Yun Yuanling.

While standing on a hill and dripping blood from her entire body, she looked down at the world.

Such a gaze was given so naturally that it pressed down on people like some Heavenly Mandate, as if it could not dare to be disobeyed.

The martial artists were caught in an inexplicable anxiety, thus being unable to open their mouths.

"If it is like this, the plan completely falls apart, you see? Indeed. How excessively harsh. My Young Lady Ximen."

Her tone was full of fatigue.

"If you ruin the plan so blatantly, how can I take Young Lady Ximen with me? After all, everyone will try to devour you."

Yun Yuanling showed a faint smile.

"Still. I have realized you are not feeble. Enough that you can be left alone for a while."

At the same time, she took something out of her bosom.

It was a bundle of bells tied together.

"Then. It is time to withdraw. Will those affiliated with the Association please gather here?"

A group of martial artists burst out from the main stronghold.

When the bells jingled and jangled simultaneously, Jiangshis followed with strange hops behind such people.

And among the water bandits led by Waterway Forts Commander, Bu Xiayun, more than twenty of them were Jiangshi that had defected.

Sighs mixed with astonishment spread here and there when a comrade with a calm face turned out to be a disguised Jiangshi.

"Congratulations. Members of the Waterway Forts. Today, you have avoided a great disaster, thus extending your insignificant lives a little longer. You may feel free to rejoice."

The five Heavenly Jiangshis courteously lifted Yun Yuanling and carried her away.

As she slowly disappeared over the hill, only her voice vividly penetrated the ears.

"Please. Be grateful for your fortune and enjoy the remaining moments of your life. After all, there will not be a next time."