\chapter{The Waves in Front of the Yangtze River Are Like This and That (3)}

The splendidly set table was less substantial than it appeared.

The food, prepared in advance, had cooled to a tepid temperature.

The alcohol was bland, almost lacking in its toxicity.

Yet even so, Qing was extremely satisfied.

Because it was free!

Moreover, was it not something everyone could understand?

No flammables allowed on boats.

No drunkenness allowed during water activities.

Qing wolfed down the food.

If Ximen Surin had seen this, she would have been horrified, thus launching a nuclear noogie carpet bombing operation.

This was how a beauty of Zhongyuan was supposed to eat.

\begin{quote}
	Pick up a morsel as tiny as a sparrows tear and gently place it in the mouth.
	
	Chew with small movements of the jaw, lips slightly pursed.
	
	And then, swallow with a somewhat exaggerated motion.
	
	Maintain a facial expression that slightly furrows the brows to avoid any wrinkles.    
\end{quote}

This was the dining method of Xi Shi, the Most Beautiful Woman in History, said to possess a transcendent beauty that would never be seen again, whether in the past or the future.

Ximen Surin was armed with a strong, self-reliant nuclear arsenal to indoctrinate Qing into this elegant dining method.

Thus, Qing could also, obviously, perform this dining method, rumored to be the epitome of beauty.

After all, there was no such thing as strong in the face of the all powerful whip.

If there was someone who could stand firm in front of a whip, perhaps it was worth considering that the whip was lacking, rather than the person being exceptional.  

But Ximen Surin underestimated Qing too much.

Her understanding of human correction was slightly lacking.

Honestly, her idea of instilling manners and grace as habits was revolutionary enough to make all the teachers of Zhongyuan leap to their feet, in a frenzy to learn such sacred ways.

The result of such an avant-garde was Qing.

Qing could now perfectly perform forty-two different hairstyles.

She had reached a realm where if it felt slightly loose, her hands would automatically move to fix it.

Her stride slowed, no longer walking as if there were two huge bowling balls of steel hanging from her crotch, and her movements became more leisurely and feminine.

She knew how to smooth out the wrinkles in her clothes by using Inner Qi and sew up a burst seam neatly.

But habits were ultimately in the realm of the unconscious.

There were desires that surpassed the unconscious, so some actions could never become habits.

For example, preferences.

Qing originally loved the feeling of her mouth being fully stuffed with food, at the point of bursting.

She was only suppressed by nuclear noogies, but now that she was free, there was no need to hold back.

Even Che Nanzhong was slightly awakened by Qing's all too hearty manner of feasting.

"Damsel, please eat more slowly. There are other dishes too."

"Ah, I'll eat those too, so its okay."

"...?"

{\itshape Didn't she say she was a female martial artist?

Was she some fucking beggar in disguise? Did everything she ate go straight to her chest? How can she eat so fucking much?}

Che Nanzhong's anger began to rise.

\textit{What kind of bitch was this?!}

She didn't have coquetry or charm. She did not even have a hint of desire to act cute to him.

Basically, she wasn't trying to sweetly curry favor as an attempt in becoming the daughter-in-law of a Regional Inspector!

If so, this wasn't fun at all.

The moment when the mask worn through seduction was stripped away was crucial.

It was honestly pleasing if they cursed and resisted, or better yet, cried and begged for their life.

But with her mind so completely engrossed in solely the food, how could he not be furious?

Che Nanzhong was positively seething inside.

However, as Qing started to enjoy the alcohol after sufficiently filling her belly up, his wrath disappeared as if it never existed in the first place.

The way Qing leisurely sipped her drink, void of any hurry, was the part least needed to be corrected by Ximen Surins harsh nuclear noogies.

Moreover, Qing had mastered the White Hand Demonic Arts.

One might wonder why Demonic Arts had anything to do with the Dao of Alcohol, but one of the characteristics of White Hand Demonic Arts was the beautiful shape of the hands.

As thin and slender as a sliver of jade; the most elegant and beautiful hands, yet also the most cruel.

This phrase was inseparable from the description of White Hand Demonic Arts.

The skin of the hands was so pale it was almost transparent.

The slender and long fingers that gracefully wrapped around the cup embodied liquid beauty.

The side profile of Qing, leaning against the railing and sipping from the cup, exuded a devilish charm that bewitched men instantly.

Che Nanzhong approached with a lecherous smile, feeling the awakening of his alter ego.

"It seems like the alcohol suits your taste?"

"I would have preferred it to be something stronger, though."

The alcohol was so bland that it hardly even resembled alcohol.

"Well, that is obviously because I hoped the Damsel wouldn't get too drunk. A woman who is drunk and confused is no fun at all."

"Fun? What kind of fun?"

"Well..."

The men on the deck started to stand up, slowly approaching her way.

Then, the men surrounding Qing drew their swords.

"Ooh."

Qing steadied her racing heart.

\textit{Is it finally starting? Are we going to kill each other now?}

"One ke\footnote{Ancient Chinese unit of time. 1 ke = 114.4 minutes}. I'll give you just one ke."

"One ke?"

"We will leave after one ke, so try to run away wherever you can. If you can hold out for just half a shichen, we will let you go safely. I promise this."

"And if I can't?"

"Then you shall be sharing cloud and rain\footnote{an expression for sex. Originated from a poem called Gao Tang Fu by Song Yu} with all of us today."

\textit{Ooooh. This isn't the skill of someone whos planned this only once or twice before, huh.}

Qing was pleased. Very pleased.

\textit{Then, I, too, can enjoy myself without worries.}

"Ah. By the way, I would not recommend jumping out of the boat now. This is the Three Gorges, after all. It would be an exceedingly painful way of ending yourself."

The Three Gorges was famously treacherous.

The water flowed differently above and below, with plunge pools rising and falling throughout the entire area.

It was to the extent that even the river water was discolored due to such a phenomenon.

The waters were so rough that even skilled martial artists could not swim through without being swept away.

"Hmmm."

Qing slowly walked forward.

The men holding swords tilted their bodies to make way.

It wasn't that they were stepping aside, but more as it to say, 'Try rubbing your body on us if you wish to pass by'.

Qing did not pass through them.

Instead she grabbed the blade of a mans sword with her bare hand.

And then, as easily as plucking a flowered branch, she snapped the sword in two.

Qing clenched and unclenched the hand that held the blade.

The sword, crumpled long and thin, clattered to the ground.

The previous atmosphere of ridicule from the men froze instantly.

Qing examined the palm that had crushed the blade.

There was not a hint of a scratch or a bruise left.

Only then did Qing smile in satisfaction.

{\itshape That's right. This is the shit.

  This is why I just have to learn Purple Martial Arts.}

"Well, then. You saw that, right? You motherfucking rapists. How fucking ridiculous. What are you, a circus? What the fuck do you mean run away when were on this cramped ass ship? Should I jump into the sky or something? Or into the grou- ah right, there is no ground. Anyway. To think that fuckers with cocks attached to them would resort to this instead of trying to confess directly and proudly. You're making me look like a total slut. I'm so embarrassed."

What on earth was happening?

The men's gazes shifted between Qing and the twisted metal that was once a sword.

"The heck? Still haven't come to your senses? You little pieces of shits."

Qing's hand shot up then fell down.

Her four fingers smoothly burrowed into the top of a man's head.

Passing through the skull, it scrambled the brain. Literally.

From the eye socket to the cheekbone, across the upper jawbone and teeth, reaching all the way down to the lower jawbone.

The fingers, which were gently pulled out as if scooping fine sand, emerged in front of the Adam's apple.

The man with four deep grooves carved into his face collapsed.

His body twitched.

It was because of the remaining nerves, not yet dulled, trying to desperately send signals to a nonexistent brain.

The corpse's head showed four deep wounds.

The innard's swelling from there protruded in a bumpy manner.

\textit{Oh my world. Oh my, oh my.}

Qing shuddered.

She had gone inside and came out of someones head with each one of those long and slender fingers in all its entirety.

It was not some figure of speech.

It was actually a literal, physical intrusion.

From that, she felt deeply moved. After all, there was that profound sensation of digging into bone.

Warmth spread from her dantian throughout her body.

A rush far sweeter than what any bland alcohol could provide electrified her nerves.

{\itshape There really was a difference between using a sword and bare hands.

  Its like the difference between picking my nose with or without gloves, huh.}

Practically in ecstasy with how pleased she was, Qings smile stretched so wide it almost reached her ears.

"Do you still not understand the situation? You're not gonna run? Good. That's right! Go! My Moonlight Sword...is over there. Let me try that again."

Qing clenched and unclenched her fist as she spoke again.

"Well then, my Moonlight Hand is starving. Ready or not, here I come~"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Che Nanzhong couldn't make sense of the current situation.

-Where did it all go wrong? What is she? What is wrong with that bitch! Is that even human? She's a completely crazy bitch!

-It seems we have messed with the wrong person.

-What are you even doing there?! She's just a fucking woman, isn't she? Why are you not going out to confront her? Just kill her. I don't even want to touch a filthy woman like that. I'm not shagging her.

The guard cringed, bowing his neck. 

-Young Master, that female is truly formidable..

-What did you just say? Then are you a fake Master? She's just one bitch, isn't she? Do you even see how many armed men we have? Who does she think she is?

-Young Master, when a person strikes someone on the head, isnt it normal for it to crack or burst? 

-Of course. What an obvious question.

=But that female scooped out flesh and bone like clay. That can't be done even if using a blade.

The guard trembled.

Even if it were possible, actually doing it was an entirely different matter.

It was clear from his appearance that the guard was utterly, truly terrified.

Only then did Che Nanzhong realize the gravity of the situation; his anger faded, leaving only a face pale with fright.

-W-What is that supposed to mean?

-We can't win against her. Not even if all of us combine. It is absolutely impossible. We touched the wrong person.

-What? What are you saying?! You were the one who said she looked soft!

-That is not what is important. The important part is that even if she is a Master of Wulin, she would think twice before making an enemy out of a Regional Inspector.

Che Nanzhong turned pale and quickly interjected.

-Then?

-First, let us try to soothe her gently and then lure her with wealth. Judging by the way she gorges herself, she seems to be from some poor sect, so it should definitely be possible to settle this with money.

-Really? It should be, right? 

That was when it happened.

Knock, knock, knock. The sound of someone knocking on the door.

-Excuse me, are you in there? I'm pretty sure I heard voices coming from this direction

Che Nanzhong and his guard covered their mouths.

-Maybe not? Did I hear wrong.

After murmuring, 'That's weird', silence ensued.

After a while, the two naturally lowered their hands from their mouths.

Suddenly, fingers naturally sprouted from the cabin door.

They slipped through without any sound, as if passing through the door.

Soon, the fingers moved downwards.

A long crack trailed behind them like a tail.

The two exchanged hurried glances and stuck close to the wall where the door was attached.

A terrifying presence was felt beyond the door.

It was an overwhelming killing intent.

-There's actually no one, huh? I just waited for no reason. What a waste. I thought they were just pretending not to be here.

And then, the sound of footsteps slowly faded away.

For a while, the two mimicked statues once again.

Only after one ke had long passed did they finally catch their breath.

-Is that a human or a ghost?

-I do not know. Jianghu truly is vas...

The guard suddenly stopped talking.

-Young Master.

-What?

-When walking inside the ship...do footsteps make a sound?

-Wouldn't there obviously be the sound of footsteps when walking? Why suddenly?

-That...Usually, we would hear the creaking of wood.

-Huh?

Both froze at once.

Cold sweat broke out, pouring down like a waterfall.

Their necks creaked as they turned their heads towards the door.

And then, through the long vertical hole in the cabin door

Their eyes met the gaze of someone watching them.

"\~{}Found you\~{}"