\chapter{The Waves in Front of the Yangtze River Are Like This and That (1)}

\textit{Ximen Qing, Charge!}

...was what she was about to do, but Chen Changming clung tightly to her.

\textit{Hold Charge.}

"Sister. Don't go."

"I'm not going away forever, you know? If you act like this, it feels like I might never come back or something."

"What the... You were gonna come back?"

"I'll be coming and going. Why would I leave the house I've set up for myself for the first time in my life?"

Qing thought of her own thatch.

It was an old house, with just one room, a veranda, and outdoor the kitchen.

\textit{But it was my house.}

That resonance had a great emotional impact, piercing through the heart of a modern person like her.

"You're coming back, right? For sure?"

"Yeah."

"For sure, for sure?"

"Don't keep adding for sure. Just because you're a bit pretty now doesn't mean you can act cute all you want, okay?"

"Tsk."

"I'm thinking about whether I should come back in winter. It's a bit tough to move around when it's cold, after all. Anyway, keep training hard."

"By then, I bet I'll be at the Transcendent Realm."

"Okay buddy. Next First-Rate Nobody please."

Chen Changming let go of her hand when she heard her promise to return.

"Great Junior Grandmaster! You must come back!"

"Great Junior Grandmaster! Please be careful!"

"Great Junior Grandmaster! Bring something delicious when you come back!"

"Me too!"

"Me three!"

The sect disciples who came to see her off were making a racket.

Ximen Surin did not come out.

But in reality, Qing had already given her a grand bow while bawling her eyes out.

In hindsight, there was no need to go that far, but she got carried away by the atmosphere.

It felt like that was exactly what needed to be done.

'Cry now, just like in a K-Drama!' was kind of the vibe she got.

Anyway, she received a new sword with the tears as its price.

{\itshape Moonlight Sword (No. 8), welcome back!

At any rate, Ximen Qing, Charge!}

Qing stomped out of the mountain gates boldly.

And then, she immediately opened the Righteous Rewards.

There were things that needed to be handled quickly while still feeling this sense of belonging and regret.

Bringing Chen Changming along had given her a huge boost in Righteous Karma, now totaling over a thousand.

And at a thousand points, another exchange could be made.

Since she was unable to add a new martial art until now due to her Teacher, a Supreme Master of oriental medicine who could diagnose with just a touch of her fingers, now was the perfect opportunity.

Qing still remembered the terror of facing the Sword Force of a Transcendent Realm Master without a sword.

That was why she needed a martial art that could be used without a sword.

A very, very powerful one.

Fortunately, she had already heard of one.

White Hand Demonic Arts.

If the Grand Star was reached, everything below the elbow would become indestructible.

A rocket punch that could block even Sword Force!

A brilliant Purple Border guaranteed its strength.

Qing immediately received the Righteous Rewards.

The sutra for the White Hand Demonic Arts embedded itself in her mind.

No matter how many times she experienced it, this Brain Engraving Memory Method felt absolutely filthy.

However, she no longer had enough Practice Points to completely master a Purple Martial Arts.

Qing raised the realm of the White Hand Demonic Arts to 6 Stars.

It was quite a frugal investment.

Strangely, martial arts tended to get significantly stronger at 6 Stars, after all.

Using the martial art would accumulate Practice Points anyway, thus allowing her to reach the next stage.

And there wasn't any particular need to excessively invest her precious Free Practice Points.

She still had some Free Practice Points left, albeit a vague amount. There wasn't anything important she could do with it.

As such, she raised the 2 Stars Buddhas Palm to 6 Stars.

Where else should I use the remaining points?

{\itshape Just as expected, there is nothing as enjoyable as planning a character build-

Character build?}

"GAME ADDICTIONS STOP! I LOVE REALITY! GROSS. IT's SO GROSS!"

Qing shouted hastily.

She had let her guard down for a moment, leaving her in this state.

Qing's hands trembled uncontrollably.

{\itshape I just had a fairly touching and, more importantly, human farewell.

But to think I would come out and do this immediately. Again. All over again.}

Qing immediately attempted to gaslight herself as a way to defend her mental state.

{\itshape Everyone, this is how harmful game addiction is to the brain\footnote{Korean meme}.

I have tried turning everything off for a moment\footnote{Another Korean meme}.

That's the criteria of those who have experienced the original Kartrider\footnote{Yet another Korean meme}.

That was the customers individual choice and I don't think of it as harm\footnote{Uma Musume meme}.

It's okay to lose the match against RGE, the important thing is an unbreakable heart\footnote{League of Legend meme}.

That's right! 

What matters is an unbreakable heart! An unyielding spirit!

Sensei Deft, thank you.

But you know, I heard you never actually said that, yeah?}

"Hoooo..."

Qing let out a deep sigh.

She couldn't take it anymore. Extreme measures were needed. It was a means that she could only do now.

Qing turned around.

{\itshape Oh well. It can't be helped.

Guess I'll have to stay one more day at home.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Chen Changming's childhood was blessed.

Now, it was nothing more than a bitter memory.

After all, all her fortune was from money stolen from the sect.

Anyway, for the frail Chen Changming, her parents hired a retired local government official to be her writing teacher.

The tutor always emphasized the importance of words.

He said that words were more precious than gold and could sometimes save a person's life.

Chen Changming disagreed.

'If words can save a person, why am I in this state? How dare you pay lip service when you don't even understand the other's circumstances?'

By then, Chen Changming was already aware of the severity of her illness.

The writing teacher was fired soon after and Chen Changming learned the reason later from overhearing her parents conversation.

He had apparently once gotten drunk, failed to recognize an Inspector, and hurled curses at him.

Thus, it led to his dismissal from his government post.

The writing teachers words were not mere lip service.

They were filled with genuine sincerity.

If words could save a person, then words could also kill a person.

That was probably what the tutor was thinking when he spoke as such.

A very, very old memory. A memory that she didn't even need to remember.

But she recalled it suddenly in that cold, dark tunnel.

'You did nothing wrong. What can you even do about the way you were born? All you can do is call it bad luck and move on. Did you ask to be saved? No, right?  Tell them all to just fuck off.'

From that moment onwards, Chen Changming wholly agreed with her past writing teachers sentiments.

The words lifted the burden she felt in her young life; a burden so heavy it even made it hard to breathe, pressing down on her chest.

As such, Chen Changming decided not to think too much about her parent's actions. 

She still loved them, but honestly, she didn't want to see them anymore.

On the other hand, living as a disciple in the Divine Maiden Sect meant spending a lifetime with other women.

Was that perhaps why? Chen Changming witnessed many, many bizarre scenes.

Senior Sisters and Junior Sisters locking fingers and striding together, paying no attention to anything else but each other.

As a sickly child, Chen Changming was quite quick at noticing many things.

That wasn't just a sign of friendship.

Friendship only consisted of hugging one lightly, saying how cute one was, or linking arms.

Friends did not lock fingers tightly in an unspeakably in, inde, indece, indecent manner.

Each time she saw this, Chen Changming would recall that dark pit.

That cozy darkness.

That warmth that heated up her body.

\textit{She hugged my small body tightly, really tightly, so tightly, very tightly, like really right up close, with like heartbeats thudding loudly and like incredibly soft and fluffy skin rubbing against skin and-}

It was then.

"Heyo, Ming. I've decided to stay one more night."

"...?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After receiving a grand send-off, Qing left the Divine Maiden Sect and returned in half a shichen\footnote{Ancient Chinese unit of time. 1 shichen = 2 hours}.

Everyone's gazes meeting her's was beyond embarrassing.

However, mental health was important.

Chen Changming's gaze upon their quick reunion was peculiar.

It was as if she was thinking, 'What the heck is wrong with this person?'.

Qing was slightly hurt by this.

Nevertheless, Chen Changming showed a truly commendable spirit by saying she wanted to spend the night together since Qing had to leave tomorrow; this kinda remedied the hurt she got earlier.

But regardless of that, Qing, shocked by the very idea of sharing a bed with a Female Middle Schooler-chan, had sent her back.

And once again, Ximen Qing, Charge!

Qing, refreshed by the spirit of having her own home, set out once more.

She had already decided on a destination the night before.

A seasoned person of Jianghu always made plans.

And Qing was now a seasoned person of Jianghu.

For now, she would go to a city.

Then, she would join any escort group and receive VIP treatment from them.

It was a perfect plan, no matter how she thought about it.

Where she went was not important.

What mattered was what treatment she would get.

And there was a city near Mount Wu.

Zigui. A port city attached to the Yangtze River.

Ximen Qing had visited the city several times before.

The Divine Maiden Sect was not a feminist self-sufficient community.

Like any other sect, they leased out their fields and paddies as sharecropping and received donations from those who came to burn incense at their sect, albeit limited to females only.

However, they were at a disadvantage compared to sects of the secular world because they did not receive a large income source in the form of protection fees.

Strangely, the Divine Maiden Sect was still quite wealthy.

How?

By selling specialties.

The Divine Maiden Sect was a Mystical Sect worshipping the Yan Emperor and his third daughter, the Divine Maiden.

In modern terms, the Yan Emperor was like a Sun God, as well as a god of agriculture and craftsmanship.

Supported by farmers and craftsmen, he would one day become the most revered god in Zhongyuan!

Therefore, the Divine Maiden Sects specialties were rumored to be miraculous. Almost magical.

Talismans, written prayers, embroidery thread, amulets, pieces of clothes with Buddhist writings engraved, etc.

With the money earned from all that, they bought what they needed.

And also what they didn't really need as well.

After all, how could one live on just food alone?

Every fortnight, when the disciples made their wish list, sect members at an Elders level took turns purchasing the items.

Ximen Qing, being one of such members herself, had followed along a couple times out of boredom.

For private outings, they had to wear a veil over their face.

Due to such rules of the Divine Maiden Sect, she couldn't really enjoy herself.

After all, it was incredibly hot out and the veil only made it worse.

Obviously, if she spent all day following the list and shopping around, it could not be fun.

As Qing headed to the city, she swung her arms continuously.

Swish, Swishhh. The sound of air being cut was sharp.

White Hand Demonic Arts.

This rare Demonic Arts, among the top five most evil martial arts under Heaven, adorned the air.

It was so unique that those who practiced the White Hand Demonic Arts were given special, exclusive titles like White Hand Demonic Person or White Hand Witch.

It was the wisdom and will of Wulin seniors, passed down through generations; 'That fucker fucking has White Hand Demonic Arts. The bastard has to be caught and killed at all costs, you hear me?'

Of course, Qing had no idea about this. There was no way she would.

It was something even her teacher, Ximen Surin, could not have predicted.

The idea that someone possessed several Daoist Divine Arts would suddenly learn a Demonic Art was utterly unthinkable.

Even a madman would hold back their tongue and marvel, 'What an imaginative idea!', before applauding at the sheer insanity they could never hope of matching.

But Qing had accomplished such a difficult task.

While admiring the brutal and wicked power of the Demonic Arts, Qing couldn't help but to remark.

\textit{Oooh. Power Bitch Slap. Hm. I wonder if I can somehow attach fire to my hand? Would that not work?}

\vfill
\begin{lstlisting}
The chapter title is a reference to Chinese proverb, 'The waves in the back of the Yangtze River push the waves in the front'
\end{lstlisting}