\chapter{The Waves in Front of the Yangtze River Are Like This and That (8)}

The Mission Window displayed such stark words. 
\begin{quote}
[Omen, (Unknown)th Crisis]

Description:

[You stand before the downfall of the Waterway Forts.]
\medskip

Actions for Mission Completion

Righteous Karma) Assist the Waterway Forts in suppressing the rebelli-
\end{quote}
Qing immediately closed the Mission Window.

\textit{Fool me once, shame on you. Fool me twice, shame on me. You think I'ma fucking idiot?}

She wasn't interested anyway.

No matter how grand the claims about influencing everything below Heaven were, she would not be fooled again.

{\itshape What's so great about influencing everything under the Heavens anyway?

Just the fact that I'm breathing right now means I took a whole lungs worth of air from the world, you know? So I've influenced something under the Heavens, haven't I?

After all, it's better to do whatever I want than doing shitty things just to receive a bit more Righteous Karma.

Teacher, this is how your disciple lives. This is how she is doing.

I wonder how our Female Middle Schooler-chan is doing. Is she well?}

Qing ignored the Mission Window.

When she did so, it popped up again.

And Qing got pissed off. Rightfully so.

{\itshape What the fuck? Do you wanna go? You wanna try me, huh? Is that what it is?

What? You'll keep popping up until I read you or something?

Shall I show you my ability to skip through cutscenes, honed through countless second tries of games?}

\begin{quote}
[Advent of the End, Blood Calamity of the Nine Provinces, Final Chapter. The Last Crisis]

Description:
\medskip

[At the end of a long pursuit, you have finally faced the true mastermind behind a brutal conspiracy. It is the destroyer of all who breathes under the sky, as well as the end of the world.]

For the sake of the world, eliminate Yun Yuanling

*Blood Poison) Massacre all who stand with Yun Yuanling

[The fate of all under the Heavens depends on you.]
\end{quote}

But the words written were very different from before.

Moreover, it was a format she had never seen before.    

As Qing scrolled through the Mission Window, she saw Yun Yuanling's name.

Final Chapter. The Last Crisis.

The destroyer of all people, as well as the end of the world.

{\itshape So, that means she's the End-Stage Boss?

Why the fuck is the Final Boss appearing now?

The Mission Window said to meet after a long pursuit, didn't it?

Is this a bug?}

Qing suddenly felt rather cheerful.

Qing just wanted to enjoy a delicious dinner and incidentally see some bloodshed through the process.

Like a ship without its rowers...No, it was actually a ship without its rowers. Anyway, along with such a ship, she had drifted here.

Qing was unaware of any conspiracy.

She didn't even know that the existence of some mastermind or whatever existed in the first place.

She especially didn't realize she had an enemy she needed to pursue.

And yet, something like this was being oh so proudly displayed. Why? She didn't know. To reemphasize, she didn't know shit.

{\itshape Mission? That piece of shit.

If this is the result of some stupid calculation triggered by something, well, fuck it. Who fucking cares.}

"Hey. Ah-Yuanling\~{}\~{}, Ah-Yuanling\~{}\~{}."

"Oh my. Is that? Are you calling me?"

"Eung. Why? You don't like it?"

"How can you suddenly be so bold? Your trembling figure was quite cute before."

"So, does that mean you dislike it or something?"

"No. Not at all. It is quite to my liking. Have you opened up your heart?"

Yun Yuangling smiled brightly.

Qing smiled back and asked.

"You said you'd protect me, right?"

"Of course. As long as I am here, you are the safest person in this world, you see?"

"But the fact that you need to protect me means there are also dangers that are that severe, right?"

"After all, there are about three Living Jiangshis and quite a few Blood Jiangshis. Above all, since the Demonic Cannibal has directly intervened, the frail Young Lady Ximen will not be able to last more than a few strokes. Isn't that so?"

\textit{Demonic Cannibal? Feels like I've heard of the guy before.\footnote{Chapter 18}}

Qing repeated the name a few times, then gave up on remembering.

{\itshape Must have heard it somewhere along the way. Whatever.

But his name is the Demonic Cannibal? Wow! What a shitty nickname. Did his mother not love him?

I can't believe he's such a piece of shit that he's actually known for eating people.}

But there was something more important than that.

Qing smoothly asked another question.

"So, do you really like me that much?"

"Words cannot fully express how much. You cannot even imagine what you mean to me. What kind of existence you are to me."

"Why? Is it because my Constitution is unique?"

Yun Yuanling's eyes widened.

It was a dramatic change from her usually graceful demeanor.

"Did you already know?"

"I just found out. Anyway, if another person like me appears, does that mean I become unnecessary?"

Yun Yuanling smiled with that expression.

The very expression that seemed to say she found Qing really, truly adorable.

"Oh my. Young Lady Ximen. You must understand how much of a miracle, how wonderful your body is."

"A miracle?"

"It is like counting to the tens of billions once, and then repeating that another tens of billions of times. That is what you are."

"So, I'm the only one in the world?"

"That is correct. There is only you."

Qing nodded as she fell into contemplation.

{\itshape As expected, this really kills any and all interest I had in her, huh. What a sick bitch.

At the very least, if you want to get close, you should say something flattering.

Instead, she directly stated that my body is the ultimate goal for her?

Nobody would ever be happy to hear that.

Anyway, it seems I can fuck around a bit, huh. I don't have to be too worried around her.}

Qings ability to read between the lines had completely pushed Yun Yuanling into the category of an extreme pushover. 

{\itshape This is all because I created my character well.

By the way, it seems like I'm in your debt again, Mr. Strategy Guide, huh?

If I ever return, I will reward you greatly. My life has been saved several times thanks to you, after all.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Champions of the Yangtze River, listen! Some curse us as thieves while others call us parasites, disgusting leeches living off the water. 

But is that really the case? 

There might have been a time where we were like that. When we were merely barbarians, bandits on a river, I saw pillagers on the Yangtze, witnessed blood flow along with the water, and ultimately lost my teacher to the grief and grudges it caused. Being the child of a thief, even my mother was practically akin to stolen wealth. What such a child learned from that was only hatred and twisted killing intent. The father was shameful and the child was full of loathing.

This pain was what caused us to change! But we have changed now once again! Who established the laws of the Yangtze River and put them in order? It was us. Because we are the owners of the Yangtze! It was because we have become upright heroes! Champions! Fathers and mothers envied by the land dwellers because we are right! Because we are just!

And now, our grand cause is shaken!

The scum trying to return to the era of plunder and cannibalism have revealed their true natures! They threaten our main house! Our stronghold! Our families!"

This was what speeches before battles were usually like.

We are the good guys and they are the bad guys.

Think of your families.

Let's fight. For blah-blah something more important than life.

While listening to the speech, Qing thought.    

{\itshape That uncle can speak really well, huh.

Not just anyone can be a leader, it seems.}

Qing looked at the martial artists heated up with morale and, on the other side, Yun Yuanling, who was busy responding to something.

\textit{I really want to tell them. She's the mastermind. She's the one manipulating all of you behind the scenes. She's the one who did everything. But, so what? They wouldn't even take me seriously anyway.}

After saving the leader's son, she's been treated with utmost respect, so even if Qing said something like that, she would just be called a crazy bitch.

She was a very high-functioning nutcase. Oh, and a capable murderer.

\textit{I mean, that's probably why I was supposed to find out about her after a long pursuit.}

Qing grinned and approached her.

"Consider Jiangshis as having have no weaknesses. You have to hit their necks or cut off their limbs to immobilize them. At the very least, they are monsters that can only be wounded if one is in a realm where they can hurt people with External Qi and I can weaken the Living Jiangshis with sorcery-"

Turns out it was something like a strategy meeting.

It almost felt like she was playing with them. After all, she was the one who had empowered the enemy's ringleader, but now, she was digging into his weaknesses, exposing them for the other side.

Qing poked someone she recognized in the ribs.

It was the First Arrival of the Yangtze River, Bu Penwu.

"Hey, Uncle."

"Young Lady Ximen? What is the matter? It's a busy time right now."

"Give me back my sword. You said you'd return it later, didn't you?"

"Agh, later, okay? We are about to fight, so the Young Lady should just stay safe and wait."

"How am I supposed to be safe without a sword in my hands? If I stand empty-handed, do you think the enemies will just avoid me? Should I yell out or something? That I don't matter, so they shouldn't hurt me?"

"Ah, I see. Hey, Juhyung, in my room, theres a sword under the bed. Bring that here."

And so, Qing got her Moonlight Sword (No. 8) back in her grasp!

Not long after, an island appeared suddenly through the fog.

The main stronghold of the Forts of the Yangtze River Waterway, called Waterway Fortress, was located on that very island.

The dock was crowded with people, but it was clear from a glance that they were not there to welcome the returning heads of families.

Isn't it obvious for anyone that theyre ready for a fight? Like, they're all lined up, holding spears and swords.

Qing watched this shitshow while holding onto the railing.

Suddenly, red streaks shot across the sky.

"Fire arrows! Shields up! Firefighters, stand by!"

Hundreds of fire arrows.

With a loud noise, the fire arrows that hit the deck and hull stayed stubbornly lit and kept flickering, igniting themselves over and over.

It was chaos.

The fire arrows continued to whistle down, people were stepping on flames and spraying sand, and some unlucky ones got hit by an arrow and collapsed.

Some tried to pull away an injured martial artist only to get hit by another arrow while others caught fire and were running around in a panic.

However, the massive vessel, which seemed like an aircraft carrier to Qing, was not much hindered by this.

"We're docking the ship! Get down!"

The ship charged straight into the sandy beach; it was quite a rough and fiery docking method.

The collision caused the giant ship to traverse the beach, creating a veritable earthquake.

The stern opened and martial artists poured out onto the beach. The Masters jumped off the deck and joined the crowd immediately.

As arrows poured onto the shore, people started falling continuously.

Though there were no guns, it was quite a tense landing operation.

It was quite a spectacle to observe.

Then, a voice called out for Qing.

"Young Lady Ximen, you can wait here, yes?"

"Eh? Didn't you say you'd protect me."

"These children will protect you."

Simultaneously to those words, something that looked like people popped out from behind Yun Yuanling.

They appeared to be about ten years old. So they really were children.

But their eyes were completely black without any whites, making them eerily disgusting. They were not normal.

"Them? They're going to protect me? Are you sure it's not the other way around?"

"Ah. Despite how they look, they are incredibly strong children called Heavenly Jiangshis, you see? Each one can face a Transcendent Realm Master, so they are quite reliable."

"Ooh."

Seems like they're the Final Bosss guards or something.

Wouldn't they probably appear as mid-bosses?

"Then, let us meet again after everything is done. Young Lady."

Yun Yuanling waved her hand.

Qing responded with a bright smile.

"I don't want to, though?"

"Oh dear. Young Lady? This isn't a request, you see?"

Qing shook her head.

"The Demonic Cannibal is the strongest, right? Since you said you'd protect me, let's keep that promise, okay?"

"What-"

Ignoring her, Qing leapt down.

A refreshing free fall. The sand on the beach softly cushioned her plummeting body.

She channeled her True Qi to her feet.

As her Teacher said, her Inner Qi was already top-notch. Practically absolute.

With a massive amount of True Qi propelling her forward, it felt like the world was receding behind her.

Qing laughed.

{\itshape With the Final Boss promising protection, what is there to fear?

Haven't I already heard a confirmation?}

Qing took a deep breath.

"HEY! DEMONIC CANNIBAL! SORRY WE HAVE TO MEET FOR THE FIRST TIME LIKE THIS! BUT I HEARD YOUR MOMMY DIED! WERE YOU SO HUNGRY THAT YOU EVEN ATE YOUR OWN MOMMY AND DADDY?! "

Following that, a roar similar to a lions shook both Heaven and Earth.

"WHICH BITCH! DARES!"

It was a wrath that could be felt vividly, even from afar.

Qing glanced back.

Yun Yuanling, extremely taken aback, was running towards her, followed closely by the five children.

Each of these kids was said to match the Transcendent Realm, right?    

Qing raised her voice again.

"I AM XIMEN QING! LETS HAVE A FAIR ONE-ON-ONE FIGHT!"