\chapter{The Waves in Front of the Yangtze River Are Like This and That (4)}

Creaaaak. The cabin door opened.

A blood-soaked figure entered the cabin with a friendly smile.

Qing looked around the cabin and snickered softly.

"Oooh. I heard about this. This is that thing where a serial killer collects souvenirs, right? What a supreme motherfucker."

The scene was decorated with silk on the walls and womens accessories such as hair ornaments and clothes fasteners nailed to it.

Or maybe he had a hobby of collecting womens accessories.

Either way, it was neither a healthy nor sane hobby.

Che Nanzhong hurriedly spoke up.

"D-Damsel. Please listen to me!"

"Damsel? Dammmmmsel? Have you still not come to your senses?"

In Zhongyuan, the term Damsel was used for a woman who was more than a friend but less than a lover.

Young Lady was a much more respectful title than that, very similar to how one would call someone Mister\~{}\~{} or Miss\~{}\~{}.

Acting friendly and using Damsel right from the start was like introducing oneself as a frivolous man who was fond of women.

"No, I mean, Young Lady. Please hear me out. Even though we met under unfavorable circumstanc-"

"Wait a moment."

Qing interrupted Che Nanzhong.

"This body...Thinking. Wait."

"...?"

"Nah, never mind. I'll just ask."

Her eyes, which looked to have gone utterly insane, were now focused on Che Nanzhong.

"How do you want to die? I've tried this and that, but nothing really satisfies me."

"Uh, could I possibly not die at all-"

"No."

Qing cut him off decisively.

"Wouldn't the owner of these mementos feel too wronged if only you continued to live? And you have the highest number of Practice Points here. Who the hell would leave prime ribs and only eat the side dishes?"

Although he didn't quite understand what she was saying, what was certain was that she had no intention of sparing her life.

Che Nanzhong mustered his last bit of courage.

"I-If you touch m-me, Father will not sit idly by! My father is a Regional Inspector!"

A-Qing cocked her head.

"Isn't that obvious? It would be stranger if a father did nothing when his child is killed. So, what about it? Might as well get your dad to move a bit too. Middle-aged health is all about exercise. Kyaaaa, wow, wow, wow. A truly filial son is born."

"You're crazy! You're an absolutely crazy bitch! Comrade, what are you doing! Quickly! This bitch has-"

Che Nanzhong's voice trailed off as he urged his guard.

At some point in time, the two of them were the only ones left in the cabin.

"Ah, that guy slipped out quietly a while ago. There's nowhere to run away in a boat anyway. Wonder why he did that. No point."

"This son of a bitch!"

"It's okay. Just a different order is all. Whatever."

It was then.

Che Nanzhong fell to his knees and shouted.

"Please spare me! I will truly live with a repentant and kind heart from now on!"

"Ooh..."

It was a kowtow, completely revealing the crown of his head.

Qing could not help but admire that all too perfect posture.

But that was that, and this was this.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As Qing dragged Che Nanzhong by the hair onto the deck, she encountered men standing restlessly, who couldn't bear to even make eye contact.

They were all bastards with double-digit counts of Evil Karma.

Qing threw Che Nanzhong at them.

Che Nanzhong, flying into the air aggressively, landed at the men's feet, twitching.

Because, with the bones in his arms and legs shattered, twitching was the only action he could possibly do.

While leaning against the railing with a liquor bottle and cup in hand, Qing casually threw out a word.

"Cut it."

It was an unexpected command, completely out of the blue.

The men exchanged glances hurriedly, before the most undersized among them spoke up.

"By cut, you mean-"

"What else is there to cut from a male piece of shit? It's the penis. The cock. I'd rather not do it myself, you know? And you guys don't have a hobby of watching another man's thing, right?"

At that, Che Nanzhong, who was merely twitching, suddenly convulsed again.

"AHUH! AEUEUHEUH!"

The effort of a person desperately trying to speak despite having their tongue cut and jawbone dislodged was tremendous.

Even after becoming mute and disabled, it seemed like that was still precious to him.

\textit{If it was so precious, it should have been treated more preciously, you know?}

Despite Qing's polite request, the men hesitated, unsure of what to do.

Che Nanzhong was the only son of a Regional Inspector.

Castrating Che Nanzhong would be akin to cutting off a Regional Inspectors entire family lineage.

How could they possibly bear the consequences of such an action?

Qing smirked and urged them on.   

"Becoming a eunuch versus making a eunuch. Ah, if you're gonna just shut your mouth like that, then I guess it's just the former. Anyway, its one or the other, so decide quickly. I just realized I don't have to see it if I just poke with a knife."

The men startled.

No matter how fearful they were of the aftermath, someone else's thing was not more precious than their own.

"I'll count exactly to ten. One, two, three..."

At that, the men quickly rushed towards Che Nanzhong.

For a while, sloppy screams filled the air due to the absence of a tongue and a dislocated jaw.

However, the desperation in those awkward screams was all too real. 

A-Qing drank her alcohol, using the sound as a snack to enjoy with it.

Even though it was still bland, such a nice BGM and the beautiful scenery of the Qutang Gorge under the moonlight made the taste of the alcohol quite special.

"Ah. How nice..."

Life at the Divine Maiden Sect was enjoyable, but as expected, she had to cover herself in blood once in a while in order to really feel like she was really alive.

It would be nice to live all laughing and in harmony, but well.

In the end, she was a stranger.

There was actually frustration due to the harmony instead.

\textit{Ah shit. What is with these miserable thoughts when its such a good time?}

Qing shook off the souring emotions and clapped her hands.

"Well then. Now let's head to the nearest port and go our separate ways. Where's the nearest port?"

"It's Yichang..."

"Then let's go there. Come on. Let's move."

However, the men hesitated and did not move.

"Hello? Everyone?"

"..."

\textit{No way. Surely, it can't be.}

Qing tried to keep a cheerful tone.

"Anyone here who knows how to steer this ship, raise your hand!"

"..."

"Don't be shy. Just come forward confidently."

"..."

{\itshape Ah. This is a problem.

I might have killed too thoughtlessly.}

This was the day Ximen Qing got stranded.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\begin{quote}
	
Stranded Day 2.

{\itshape Those fuckers scammed me.

They said there are thousands of boats on the Yangtze River, so I could just ask for help.

Thousands, my ass. There wasn't even a single one in sight.

The bastards on the boat don't even know how to steer it.

This is truly unforgivable.

Since I didn't want to see them just loafing around when they didn't know shit, I had them clean the ship and dispose of the bodies as punishment.

The fucking idiots kept vomiting at the sight of the corpses, so it actually made more of a mess than before.

But as I kept ordering them, they seemed to have gotten used to it and started throwing them in the sea, no, the river, properly.

I finally understood the deep meaning behind why the supply officer, who was stuck on weekend duty, kept making me clean the floor with water and sundry things.

Supply Officer, I miss you.}
\medskip

Stranded Day 3.

{\itshape I found the bastard who ran away and hid.

It was quite fun.}
\medskip

Stranded Day 4.

{\itshape Still no boats today.

The banquet food has started to spoil.

It made me recall the days when I first opened my eyes in Zhongyuan.

It was a time when I had to survive on food waste.

But still, there was a certain romance in those times.

Defeating those fucking beggars and claiming the rights of a victor made me feel like I owned the whole world.

If I think about it that way, what's the big deal about a little spoiled food?

One must not lose their original resolution, yeah?

After all, it's not like I have a Constitution where I get sick from eating things like that.

Speaking of which, Half Moon Inn, you motherfuckers.

I swore I'd burn them down once I became a Master.

The day I return to Jianping is the day Half Moon Inn will finally meet its destined destruction.

Fucking hell, it pisses me off even after all this time.

I was just trying to live, you know?

But those motherfuckers took away my food to feed their fucking pigs. They deserve to die.

It's the death penalty for them.}
\medskip

Stranded Day 5.

{\itshape It seems we've entered the sea.

Its all water in every direction and thick fog makes it impossible to see anything.

They keep saying it's a lake, not the sea.

But these are the same pieces of shits who capped before, saying there's no need to worry because thousands of boats pass by every day. Right?

How can I possibly believe them?

Anyway, I bent a knife to make a hook and tried fishing since maggots started appearing in the banquet food.

It catches fish really well.

When I made several fishing hook and gave them to the fucking cappers, they seemed were beside themselves in joy.

To think they would be so happy about parasite-filled freshwater sashimi, when the banquet food was only a bit spoiled.

I really can't understand them.}
\medskip

Stranded Day 6.

\textit{Today is-}
\end{quote}

-A boat! There's a boat!

-Over here! Save us!

Qings finger stopped at the sound of the distant commotion.

She had been writing a diary for fun since there was ink and brushes available in the cabin.

When she went out to the deck, she saw the men in a frenzy.

Just moments ago, they looked like they could hardly breathe another breath, but now they seemed revitalized.

And there it was; a massive vessel appeared, cutting through the dense sea fog.

Qing was startled.

{\itshape Is that a ship or an aircraft carrier?

No, wait, did ancient China even have such technology in the first place?}

A huge ship of unimaginable size revealed its majesty.

At the same time, a resounding voice was heard.

It was a voice infused with the Inner Qi of a Master.

"How dare you defy the Fort of Yangtze River Waterway's Order of Prohibition! The audacity! You must be out of your mind!"

The Fort of Yangtze River Waterway was a group that managed the Yangtze River.

In other words, they were also referred to as water bandits.

The Waterway Fort claimed they were the owners of the Yangtze River.

The Order of Prohibition was a prime example of this.

It meant that no boat could pass through the Yangtze River without permission, a bold statement that only the true owner could make.

Of course, official ships of the authorities were an exception.

If an official ship was touched, a fleet armed with the latest cannons would descend, utterly destroying the Waterway Fort or whatever it was.

For that same reason, the Order of Prohibition usually lasted only about two days.

If they caused trouble beyond that, they would taste the wrath of the governments latest cannons.

But it was only said to last two days; considering that no boats sailed immediately after such a proclamation, the disappearance of boats on the Yangtze River could extend much longer than that timeframe.

This was why Qing was stranded and had no choice but to drift.

"You bastards! Stop the boat and kneel at once!"

However, the drifting continued even now.

After all, there was no one who could steer the boat.

"Stop, I said stop! What in the world are you thinking of doing! Damn it! Everyone brace for impact!"

The voice of the Master turned urgent.

Qing thought to herself while watching the rapidly approaching massive vessel of the Fort of Yangtze River Waterway.

\textit{Ah, I know what this is. It's a ramming tactic, huh.}
