\chapter{The Waves in Front of the Yangtze River Are Like This and That (5)}

Qing abandoned ship just before the collision.

After all, it wasn't even Qings boat anyway.

As she lightly jumped aboard the massive vessels deck, she saw people lying flat on the ground.

And then-

BOOOM!

Along with a heavy impact transmitted from the soles of her feet, the huge ship tilted significantly.

Kiiiiiiiii!

The sound of wood twisting as the ship screamed filled the surroundings.

But a Master would not falter to something like this.

In fact, there were quite a few people standing firmly, now examining the mysterious woman who appeared with the collision.

And those stares, as well as the glint in their eyes, were not kind whatsoever.

Faced with hostile glances, Qing quickly surveyed her surroundings.

She wanted to know if this was a rescue ship or if she had escaped one danger only to end up in another villains den.

The Karma of some bastards had fallen to rock bottom while others managed to maintain their Righteous Karma.

Excluding a few extreme cases, the average level was decent enough to be considered akin to an inn.

At that moment, a tall strongman, standing at the bow, pointed a harpoon at Qing and growled.

"To think you would dare to touch the Fort of the Yangtze River Waterway while in their turf. Moreover, you even dared to board this Dragon King Vessel. For that boldness alone, you are a woman to be commended."

Qing was aware that the situation could easily be misunderstood.

However, she also believed it wasn't her fault.

Didn't the boat just drift and crash on its own?

It wasn't like Qing had charged in manly, shouting, 'Ram em!'. Of course, she did want to try that, though.

But the collision just now was not intentional.

Qing believed that most misunderstandings could be resolved through honest conversation or through manipulation and fabrication.

And she had also learned the art of honest, sincere conversation from Ximen Surin.

Her experiences consisted of dealing with Third-Rate vagabonds of the back alleys, who could not be polite even if their life depended on it. Therefore, through numerous nuclear noogies, she had finally learned how to properly maintain the sophistication of a martial artist.

"This young child is-"

\textit{Still, saying young girl was a bit much, wasnt it?}

"-named Ximen Qing. I am grateful for your lifesaving grace."

Qing then bowed with her fist to her palm.

The tall strongmans signs of anger seemed to subside a little.

This made Qing feel a bit more at ease.

"Lifesaving, you say. What does that mean?"

"Regarding that...They said they would treat me to a meal, or rather, treat me to a boatride, but those fuckers, I mean, those bastards, I mean, those individuals? No, maybe it's those people? Anyway they were sons of bitches."

Her forced refinement in her speech returned to the habits during her back alleys as soon as the tension eased.

The intense experiences of fighting over food waste with beggars were far too strong for her to simply forget.

Above all, Qings attitude towards the world was not particularly serious either.

Qing finished her story.

It was roughly about how those fuckers were pieces of shits and she was entirely innocent as she had merely gotten swept up in their disgusting acts.

The tall strongman, also known as the First Arrival of Yangtze River, Bo Penwu \footnote{波本無; lit. 'Wave root void'/ 'wave with no origin'. Pa Bonmu in the original text}, fell into a dilemma.

Judging from the story, it seemed harsh to blame her.

Luring someone onto a boat for cruel acts was a well-known trick since ancient times.

It was why legends of water ghosts were passed down by every famous river and lake. 

On top of that, Qing's peculiar manner of speech and attractive appearance shone through.

A pretty young girl was arguing furiously with poorly feigned politeness.

Didn't that mean she was clearly a runaway girl from a noble clan, naive to the ways of the world?

The unique mystical aura in her eyes was something that could only be gained from those who had learned the Inner Qi Cultivation Techniques of Daoism. As such, this significantly added to that misconception.

Moreover, Bo Penwu was a father of two daughters himself.

He found it hard to be harsh on a clueless young girl who had just entered Jianghu for the first time.

"Hmhm, well, men are usually like that, so you have to be careful. It is ultimately your fault for following just any bastard and ending up in such a state."

At some point in time, the hostility had all but disappeared.

It was only then that Qing could ask comfortably.

"So, on that note, can you drop me off at a nearby city? By the way, where are we exactly?"

"It is Dongting Lake."

"What? Dongting Lake? How in the...?"

Qing swallowed the latter part of her words.

\textit{How in the world could a lake be called Dongting Lake?\footnote{It only make sense in Korean writing. Dongting lake is Dongtingho 둥팅호, while a NK politician was named Tongjongho 동정호}}

Bo Penwu, misunderstanding her silence, passed it off as her being shocked at drifting so far away.

More importantly than that, there was a crucial detail in her story he had yet to hear.

"By the way, you said that piece of shit was the son of a government official. Did he not say who his father was?"

"Inspector? Surveillance Inspector? Something like that."

Bo Penwu's heart sank with a thud.

"Regional Inspector."

"Yes, that's right! I think it's that."

"Fuck, shit, idiot-"

Bo Penwu spat out an unending stream of curses.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Fort of the Yangtze River Watery were a group of river bandits, a band of thieves.

Or at least that was the case during the time of the previous Chief Fort Boss.

The current leader of the Waterway Forts, Chief Fort Boss Bu Xiayun \footnote{卜下運; lit. 'Divination no luck'. Bok Haun in the original text}, also known as the Smiling Comrade, knew that their business was on the edge of a knife, in danger of being shut down at any moment. 

It was because of the government.

The day the authorities began it's suppression would mark the end of the Waterway Forts.

Cannons were the exclusive property of the government, and in a naval battle, if only one side had cannons, it was not even worth considering it as a fight.

From what Bu Xiayun could see, the Waterway Forts were barely squeaking by due to the governments patience.

Therefore, Bu Xiayun transformed the Waterway Forts.

They actively established relationships with the authorities to protect official vessels and manage ferryboats as a proxy of communication.

They also conducted inspections to assist in the capture of criminals.

Fighting smugglers had always been their job. After all, smuggling was a business only the Waterway Forts could do.

Worried about the governments gaze, they significantly lowered the toll fees.

As a result, the cargo volume on the Yangtze River surged, which, in turn, led to much higher revenues than before.

Such efforts bore fruit and the Forts of the Yangtze River Waterway became more like a business entity managing the Yangtze River than a group of river bandits.

They became the true owners of the Yangtze River, recognized by the government, albeit unofficially.

But then, the son of a Regional Inspector died.

The issue was who exactly was responsible.

Qing claimed that Che Nanzhong was still alive before the collision incident.

Though this was a slightly distorted truth, it was still an undeniable fact.

After all, even though his arms and legs had necrotized and his tongue and manhood were cut off, the thin thread that was his life was still intact.

If things went according to Qings plan, the survivors with an Evil Karma that was less than a hundred were supposed to drag Che Nanzhong around and testify to his evil deeds.

Unfortunately, they all drowned in the unfortunate accident.

If so, who should bear the responsibility for the death of such a dignitary's son?

Bu Xiayun furrowed his brows.

{\itshape Just when things were complicated enough, another incident occurred.

I knew that perverted, murdering, piece of shit, sex maniac would cause trouble someday. But I didn't expect this to happen.}

Che Nanzhong had been active in the Yichang basin of the Yangtze River.

And the Waterway Forts knew everything that happened on the Yangtze River.

From the ships managers to the dockworkers, practically any laborer involved in setting a boat afloat had some kind of tie to the Waterway Forts.

"So, what did you do with that child?"

"We've locked her up in the brig for now."

Bo Penwu hesitated before asking.

"Uh, are we going to hand that youngster over to the authorities?"

"If not?"

"Isn't she pitiful? She had even gone through such terrible experiences. "

"She is pitiful, indeed. But still."

Bu Xiayun gently shook his head.

"Since she came wielding a sword, she is already a person of Jianghu. As you already know, being naive in Jianghu is also a crime. This cannot be helped."

"Ugh"

Bu Xiayun comforted Bo Penwu in a sympathetic voice.

"Who wouldn't understand how she feels like your own daughter? But do we really need to invite trouble for ourselves? That is something the Orthodox Factions should handle.'

Then, as if suddenly remembering something, he asked.

"Ah, come to think of it, have you seen that bastard, Qianzhi \footnote{欠跖; lit.'blemish foot'. Heumcheok in the original text}? After I gave him a good beating a few days ago, the boys been sulking. He refuses to show himself, even to his own father.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As soon as Qing entered the cabin, the door slammed shut.

A sudden ominous chill ran down her spine.

When she tried opening the door, it was locked tight.

Mentioning that the fucker's daddy was a Surveillance Inspector or whatever did cause the strongman's expression to freeze in fright.

But immediately after, he said he would guide her to a room where she could stay until they arrived at Yueyang, so she thought that was the end of it. But to think this would happen

"I didn't see him that way, but to think that uncle backstabbed me like this. Hmm, hmm. Should  just cut them all down? I can even outright massacre them."

Qing mimicked the famous quote of a great author she admired\footnote{'Lucky-chan Returns!', an old webtoon}.

It was the same ridiculous nonsense she had always spouted. 

But whenever she spoke such things out loud, it was either when no one was around to hear or in front of villains who were going to die anyway.

It felt somewhat embarrassing to spout such stupid shit while being entirely sane.

"Is that really true?"

"EUAHH!"

As such, when an unfamiliar voice was heard, she was genuinely startled to the point that she shuddered in shock.

"I am sorry if I surprised you."

It was a beautiful woman with a frail appearance.

Her soft voice gently enveloped her ears.

A sweet and mellow voice that seemed to be capable of soothing a weary soul.

As Qing stared at her, the beauty gave her a warm smile that pierced straight through Qing's heart.

{\itshape I see.

I really like fragile beauties, huh.

But why is she smiling for me?

No way, could this be?}

"I am Yun Yuanling \footnote{雲緣靈;lit 'Cloud linking soul'. Un Yeonyoung 언연영 in the original text} from the Jin Prefecture\footnote{modern day Ankang, Shaanxi}. What about you, Young Lady?"

"I'm Ximen Qing..."

When Qing focused on people's faces, numbers would appear before them.

Yun Yuanling was no exception to that.

Right as Qing was agonizing over how many children would be good, whether to give Yun Yuanling the Ximen surname, or whether to continue her original lineage in this ancient China, a number appeared in her eyes.

-1711. She suddenly snapped back to reality.

{\itshape A four-digit number? Is this for real?

Ah, shit.

I used to loved you, woman...}

Qing became rapidly depressed.