\chapter{The Waves in Front of the Yangtze River Are Like This and That (6)}

"So, is that really true?"

"What is."

Qing's response was brusque.

\textit{That gentle voice really did wrap around my ears, but it just had to belong to the worst motherfucking bitch under the Heavens...}

To Qing, an evil person was a creature that was okay to kill, nothing more or less than a beast.

Killing villains brought great joy to Qing.

Their deaths contributed to Righteous Karma and unexpected, sudden missions could bring in a lot of Practice Points.

They were like perfectly profitable toys.

Moreover, it was like picking up trash on the roadside, even benefiting the world a little!

However, they weren't necessarily enemies that must be killed.

If they didn't start trouble first, Qing would just think of them as bad pieces of shit and nothing more.

"You said you would massacre them all, didn't you?"

"I was just talking to myself."

"Is that so?"

Qing's answer was blunt.

It basically meant to not even think of talking to her.

Yun Yuanling cocked her head.

Her elegance truly was striking; even that single movement was enough to turn heads, almost akin to an actor.

"But-"

{\itshape Why does she keep talking to me? Was she lonely because she was all alone here?

Or is she just a really clueless, tactless bitch?}

Qings thoughts sharpened as much as her anticipation turned into disappointment.

But then, a leisurely statement snapped her back to reality.

"-why were you disappointed?"

"What?"

"At first, let's see...Mmm. How should I put it? Mmm...You fell for me? Right. Young Lady, you fell for me. Didn't you?"

"That's not the case."

Qing averted her gaze as she spoke.

"Young Lady Ximen. You know, things like human reactions eventually show through bodily signals. A suddenly racing heart. Dilated pupils. The flush that spreads on your pretty face. The gentle smile drawn by your relaxed muscles. Those are the signals I am talking about."

At this point, goosebumps prickled all over her skin.

"Young Lady, you fell for me. Didn't you?"

"Hey, look here. Let's just be quiet and go our separ-"

"But then...The love suddenly cooled down. But, did you know?"

Yun Yuanling moved very, very close to Qing. In fact, she approached right in front of her.

"You smell really good."

"Seriously, it's creepy, so stop sa-"

"Why is that the case? How can a living person have this kind of scent? How-"

Yun Yuanling took a deep breath.

Qing hadn't been able to wash properly for a week due to being stranded.

All she had was a few baths with some muddy river water. Because of that, she felt dirty and uncomfortable.

{\itshape But what is up with this fucker? A nice smell?

This bitch has completely lost her fucking mind, hasn't she?}

Qing despaired at her own taste.

Then, she abruptly had a thought,

{\itshape Was there really a reason for me to endure this?

Would I have stayed quiet if a man did this?

Have I been influenced by Teacher's feminism?

Impossible. I can't let that happen.}

Qing changed her stance.

"If you don't stop right there, bloodshed will-"

"Oh my. Are you going to show your claws? How cute."

Numerous images of swords appeared in the cabin.

As they aimed at Qing in the air, blades of Sword Force numbering two, four, six, eight...

"You do not have to count. After all, I can make as many as I want."

"Haha. You're quite the Master. Wow. Woahhh. It's Sword Force. Wow. How cool."

"Really. You’re saying things you don’t mean"

Qing immediately lost her will to fight.

And then, she assessed the situation.

\textit{These bastards weren't planning to hand me over to that Inspecting Governor or whatever, huh?}

In the first place, it made no sense for a Supreme Master to be trapped here. After all, Qing was confident she could escape this confinement.

She didn't know what would come after, though.

So, they threw her as a sacrifice to a deranged murderer at the level of a Supreme Master.

Basically telling this monster to eat her up or something to keep herself entertained.

It was a reasonable deduction in Qing's perspective.

But that didn't mean being killed by a batshit insane killer here was an option.

"Isn't it kinda suffocating here? Shall I open the door for you? There's a lot of people outside."

"Well, I don't know. May I borrow your hand?"

"Uh, about that."

A blade of Sword Force slid under Qings chin, pressing into her.

Qing hastily reached out her hand.

"Here! Here. It's just that I couldn't dare to extend my unworthy paw to an oh-so-great Master. It wasn't like I didn't want to or something."

"Now then. It's going to sting a bit. Sting!"

"ARGH! WOAAAAAAH! STOP! STOP THE SWORD FORCE!"

Qing flailed around, overreacting in abundance.

But anyone would react the same if they saw a sharp Sword Force flying towards their fingers.

{\itshape This bitch is after my fingers!

Just because I was a bit cold to her!}

Qing dragged forth all the True Qi she could muster.

\textit{If I use my White Hand Demonic Arts and overflowing True Qi, would I be able to deflect the Sword Force? Fuck, I should've saved some more Free Practice Points and fully mastered the White Hand Demonic Arts instead of focusing on the Zhu Xiang Heart Cleanse Mirror}.

Fortunately, the Sword Force that seemed right about to cut off her fingers merely pricked the tip and then melted away.

"Oh my. This is White Hand Demonic Arts? How strange. The White Hand Witch has never taken a disciple. Young Lady Ximen, how did you learn it? I definitely heard they had taken care of all the veins of the earth."

"That's..."

"You do not particularly have to answer. I was just...talking to myself. Just like you were earlier."

\textit{Was this a grudge? Did that one comment prickle her that much?}

Qing could only tremble uncontrollably.

Yun Yuanling lightly brushed Qings fingers, drawing a beautiful semi-circle with the blood that welled-up.

Yun Yuanling, having wiped the blood with her thumb, took that digit to her lips and licked it.

"Ah. I understand now. So it was like that. I didn't know it actually existed. No wonder you smell so nice."

{\itshape So, what the fuck is it exactly, you crazy bitch?!

Stop talking about things only you know!}

Qing bit back her retort.

It seemed like talking back would only lead to death, so she had no other choice but to.

Today especially, she felt an overwhelming craving for blood.

\textit{Ah. I want to cut someone! Anyone!}

Fortunately, after that, all the Sword Forces dissipated.

Qing collapsed, losing all strength in her legs.

Qing heard the murderers low laughter.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

An odd cohabitation between the two began.

To be more precise, it was a cohabitation that was extremely uncomfortable for one of the two.

"Dont be so uncomfortable. I mean no harm to Young Lady Ximen, you see?"

"Then, may I leave now?"

"No, you may not."

"Yes ma'am."

\textit{Ah. I want to kill someone, anyone.}

Qing lamented.

However, humans were creatures of adaptation. 

And even among them, Qing adapted especially quickly.

Even without Qing's unique ability to gauge situations and atmospheres, anyone could tell that the opponent showed no hostility whatsoever.

But to play coy with an unidentified Ultra-Supreme Master was something only Qing could dare to do.

"Why are you doing this to me?"

"Do you really not know?"

"What do you want from me to do this?"

"The Young Lady's heart?"

"We are someone who can never be together."

"There is no obstacle that cannot be overcome in this world."

"I don't like bad people."

"Let us try to make it work out together."

"Why aren't you saying you'll become a good person?"

"There are things that are absolutely impossible in this world."

Qing found herself nodding involuntarily.

She was a villain that had accumulated a whopping one thousand seven hundred points of Evil Karma.

Moreover, currently at -1732, the Evil Karma continued to increase even though she wasn't doing anything.

Qing could spend the next three or four years tagging along, point fingers at a target and yelling, 'That fucker is harmful! I choose you, Lingling!'.

But that was out of the question for her.

And it also didnt seem like something she would do just because Qing asked her to.

After all, this bitch had considerable perseverance. It could almost be called stubbornness.

"Very well. Young Lady Ximen must have preferences too, right? Tell me. I will match them for you. Do you like coquettish women? Or perhaps a bold and courageous woman like a true man? Or maybe a pure and lively young girl?"

"You're eliminated straight from the go as a bad woman."

"Maybe there's a taste that can surpass such a stigma. Who knows, right?"

Qing deliberately chose a type of woman that seemed least compatible with this villain.

"I like down-to-earth women."

"Mmm."

Yun Yuanling paused to think.

"I can't do that."

"No, wait, but you said you'd match anything."

"There are limits to what people can do, isn't there? Instead I'll try to match the next best thing."

"Then, a pure and lively young girl."

"That is also impossible."

"Then, a bold and courageous woman like a true ma-"

"Now that I think about it that would be a bit difficult."

"You won't be a coquettish woman either, will you?"

"Yes. That is correct."

"Then what exactly can you match?"

"However, wouldn't winning a heart with a facadebe meaningless?"

"...I'm gonna go crazy. Seriously."

"If you are going to go crazy, can you be crazy about me?"

"Agh, I seriously hate this! Go away, please!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Five days had passed since Qings confinement.

The governments army descended upon the Dragon King Vessel en masse and formed a defensive formation at the boarding area.

Following them, Che Sunduan, the Regional Inspector of Hubei, appeared.

Waterway Forts Chief, Bu Xiayun, greeted the high official personally.

"Oh Great one, to have come all this w-"

"Bring that bitch, that damned fucking bitch to me right now!"

But the father who had lost his son was already blind with rage.

He had rushed over with his troops immediately upon receiving the news that his son was dead and the culprit had been caught.

Bu Xiayun was just about to signal to his subordinate when-

"Father! I am Bu Qianzhi! The son of the Waterway Forts Chief, Bu Xiayun! I have come to fulfill the task Father commanded me to do! I am Bu Qianzhi!"

The son, thought to have run away after being scolded, suddenly rushed over, screaming at the top of his lungs.

"That punk!"

"Haiya, Young Master, why are you acting like this now! At a time when an important guest has arrived-"

"I am Bu Qianzhi! I am Bu Qianzhi! Bu Qianzhi, the son of the Waterway Forts Chief, Bu Xiayun! Father! I am Bu Qianzhi! I am Bu Qianzhi! I have come to fulfill the task Father commanded me to do!"

"What is the meaning of th..."

There was no time to even stop him.

As if being propelled by an unseen force, Bu Qianzhi flew towards Regional Inspector Che Sunduan.

Then, Bu Qianzhi's arm drew a semi-circle and Che Sunduan's arm was severed, falling onto the deck.

The Guard Captain quickly embraced Che Sunduan, pulling him back and raising the alarm. 

"It's an ambush! Guards, protect the dignitary! General Qianhu! Protect the dignitary!"

Northern General Qianhu, the leader of the troops, also sprang into action immediately.

"It's an ambush from the river bandits! Form a phalanx! "

"Protect the dignitary! Phalanx! Phalanx!"

The soldiers hurriedly moved, extending their spears.

Amidst them, Bu Qianzhi swung his limbs wildly, causing a scene.

Every time his bare body was hit by spears, the spears were actually the ones to break upon impact; a single man was confronting an arm like a deity of war.

Soldiers were thrown in all directions, vomiting blood, as chaos unfolded.

Throughout this turmoil, Bu Qianzhi did not stop shouting.

"I have fulfilled! The task Father commanded me to do! I have fulfilled! The task Father commanded me to do! Hihi, hihihihi, hihihEHEHEHAHAHAHHAHA! Long live the Forts of the Yangtze River Waterway!"

Upon witnessing what had occurred in the blink of an eye, Bu Xiayun's mind went momentarily blank.

\textit{What, what in the world is happening...}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Young Lady Ximen?"

Upon hearing her name being called, Qing turned her head.

And then, she witnessed a moment where the Karma changed.

The Evil Karma, which had gradually increased all this time in this one room, suddenly spiked right before her eyes.

\textit{-1814. What the fuck is up with this bitch?}

Qing frowned deeply.    

"What now? Stop bothering me and just get lo-"

"Thanks to you I was able to save some time. Thank you. In many ways."

{\itshape This motherfucker is saying shit only she knows about again.

I really want to fucking kill her.}

A genuine killing intent, coming from the very depths of her heart, seeped out of Qing's body.

However, Yun Yuanling just smiled beamingly.