\chapter{The Waves in Front of the Yangtze River Are Like This and That (2)}

Zigui was a port. More specifically, a port city.

Though one might question what port city existed on a river, the cargo volume of the Yangtze River accounted for a third of the entire Zhongyuan.

However, just because cities were along the Yangtze did not mean they all thrived on commerce.

Zigui was exactly as so.

Zigui had rather unsatisfactory roads extending overland and, more importantly, was closer to Yichang.

And Yichang had a major road leading out to Chongqing.

Thus, it was inevitable that where roads and water met, great development occurred.

But Zigui, neighboring the giant natural barriers of the Wu Gorges, had no reason for merchants to visit.

This Wu Gorge was considered the most beautiful among the three gorges along the Yangtze.

Thus, Zigui, situated at the entrance to this gorge, was popular with tourists.

In other words, Qing sitting stubbornly in the inn, waiting to see if any escort group would pass by, would not bear any fruit.

In fact, if one wanted to join a trading company, simply visiting the local branch of the escort group would suffice.

At Qing's level, the escort group would be beside themselves, practically crawling to welcome such a talent.

No joke, even if she told them to carry her on their backs throughout the entire journey, they would do so in a heartbeat.    

However, she would have to put up with monikers like Bizarre Female Back-Climber.

For reference, the meaning of that was a weird woman who climbed on top of ones back.

Yet, Qing was unaware of such facts.

She was utterly clueless.

In the first place, she never bothered to learn.

After all, even if she used what she knew well, she wouldn't really seek out what she didn't know.

Anyway, in Qing's heart, the inn was kind of a place of meeting.

It was utterly ridiculous, but in a way, not entirely wrong.

It was right when Qing was propping up her chin at the inn, watching tourists pass by.

A young man appeared, suddenly flashing his white teeth.

He had a very healthy set, indeed.

"Oh my, a flower without an owner seems to have bloomed here."

Qing looked around.

The inn was rather quiet and those present were of ordinary or lesser appearance.

Tourists, being fundamentally wealthy, dined in restaurants, drank tea in teahouses, and liquor in bars.

An inn like this, serving everything, was for wanderers like Qing or somewhat destitute tourists.

She didn't see anything that could be a proper flower.

Though there was no way, Qing pointed at herself just in case.

When she did so, the young man smiled with his eyes.

\textit{What, me? Actually? Why?}

Qing was a bit surprised.

"I am named Che Nanzheng. Might the beautiful Damsel grace me by revealing her name, as precious as jade?"

Qing scrutinized Che Nanzheng.

Not for any other reason. Just that-

\textit{  -598, this motherfucker, what's wrong with the state of his Karma?}

Come to think of it, she had endured for quite a long time.

Without any proper countermeasures, she could only bear the bombardment of nuclear noogies with tears. Those moments of humiliation and contempt-

\textit{But, huh. Would you look at that? There's a bastard to kill here, huh?}

Thoughts of murder flared up for the first time in a while.

Qing smirked; a chilling smile spread through her face.

"I'm Ximen Qing."

"Ah! Damsel Ximen! By the way, it appears your companions are quite indifferent."

"Why?"

"Otherwise, how could they possibly leave a beauty like you all alone?"

"I have no companions."

"Ahhh. As expected, that's how it was. To be frank, I knew at first glance. No companions would leave behind a Fairy that had descended upon this world."

{\itshape Look at this little fucker yapping.

'Whats your name? Did you come here alone?'

Ohh, did this bastard frequent clubs a bit?

What's next then? Is it, 'Want to go out for a drink?', or something?}

"So?"

"Haha, actually, I have been summoned by the Emperor and must travel to Beijing. Once I receive documents for official matters, I'll be busy, so I thought to catch a breath of fresh air before then."

"Hmmm."

Qing was nonchalant.

\textit{So, isn't that just a long-winded way of saying he became a civil servant?}

Unexpectedly, for once, Qings sentiment matched the universal view.

The martial artists of the current era tended to undervalue official positions.

It was all thanks to the great Celestial Martial Emperor.

"Actually, my father serves as the Regional Inspector. This matter too was facilitated by my father's influence."

{\itshape The fuck is with this guy.

  How is he bragging so shamelessly about securing a government position through nepotism?

  Is this the spirit I've only heard of in passing? The one that's been passed down through China's long history?}

Shockingly, Qing was right on the money!

This was the very essence of the thousands of years of Chinese history, guanxi!

A father's connection would become the son's.

Even if it wasn't something to boast about openly, it remained a source of envy and pride for everyone.

"On that note, I was thinking of setting out on a wasen\footnote{A ship without keel, but not quite flat bottom either}. If the Damsel does not mind, would you care to join me?"

"A boat ride..."

"Ah, it is not the small boat the Damsel is imagining. I wish to enjoy the gourmet food and fine liquor on a ship as grand as a palace while taking in the beauty of the Yangtze River. If you could spare a little of your time, it would be a grace of a lifetime for me."

In the end, an offer to have a drink came up. Were there actually clubs in Zhongyuan?

But it was gourmet food and liquor. And a high chance of blood.

If she refused, wouldn't it be akin to losing half of her lifes purpose?

Qing was completely taken in.

"If so, it is me who must ask you for such a favor."

"Oh, oh! Damsel! Thank you!"

"It's nothing."

"Then I will send someone to fetch you at the appointed time. Should I send them to this inn?"

Qing nodded.

"Yes. That sounds perfect."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Che Nanzheng's life was way too easy.

He was the oh-so-precious, only son of Che Sunduan, the Regional Inspector of Hubei.

A Regional Inspector was a high-ranking official belonging to the Surveillance Office of the Censorate, directly under the Emperors command.

They held immense power, capable of independently inspecting officials of the county magistrate level, making their authority tremendous.

Moreover, he was the only son of the prestigious Che Family.

Hence, Che Nanzheng could have everything he wanted just by pointing and asking.

It was the absolute worst way to raise a child.

Che Nanzheng could have anything.

So, he wanted something he couldn't have.

What could that possibly be?

Thats right! To forcibly take a woman who does not consent!

That was the conclusion Che Nanzheng drew.

And he committed his long-awaited first act of insurrection, which was immediately discovered.

After all, how well could a youth plan his first crime?

His father, Cha Sunduan, simply said one thing.

'He's a man. It happens.'

It was the moment that quite a unique form of a notorious rapist was born.

Che Sunduan actually felt a bit mortified.

Forcing himself onto a woman was something a man would naturally experience at least once, wasn't it?

So, he had let it go the first time, but it seemed the Heavens were truly indifferent to his expectations.

After all, Che Nanzheng had reached a level that was somewhat acceptable even for Che Sunduan, who loved his son so dearly.

He went into a fervent state of denial, using his authority and connections to place his son in the military, hoping that roughing it out might improve him and also curb his vile hobbies..

But regardless of such hopes, all of his crimes gradually became bolder.

Che Nanzheng, too, was similar to his fathers thoughts at first. He started with easy targets, those who weren't even worth mentioning.

But then, he moved onto married women from commoner villages, then moved onto Russian women, and eventually to beautiful women.

And now, he had even reached the level where he preyed on a beautiful female martial artist.

Qing was not particularly unlucky to be caught in his vile acts.

It wasn't the influence of the Heavenly Slaughtering Star or some fate forced upon her.

The reason Qing was up to be the next candidate was just because she was somewhat suitable to be.

Despite being neatly dressed, wearing old clothes and sitting in an inn in a city meant for sightseeing was no different from declaring poverty.

After all, how skilled could a poor swordsman possibly be?

Moreover, her face was pretty enough to be considered beautiful.

"Kekeke, did you see her reaction? She pretended to resist but came over as soon as I mentioned Father's name. Shall we bet on what kind of reaction she will have?"

Che Nanzheng gossiped with his guards on top of the wasen.    

"I bet one liang \footnote{Chinese unit of weight. 1 liang = 37.31 grams. The silver sycee usage is implied here} that the girl will cry and collapse in a heap. She looked soft, after all."

"I'll bet on that too."

"Tch. That kind of bitch is no fun, though. It would be more interesting if she curses and creates a scene."

Their conversation was absolutely outrageous.

"But still, she claims to be a martial artist, does she not? Female brats who pretend to be martial warriors are usually as tough as men, Young Master."

"That's right, isn't it?"

Che Nanzheng snickered, puffing up his lower garment.

It was about time for the servant he sent to fetch her to return.

Che Nanzheng licked his lips.

All while utterly unaware of what he was inviting.

It was time to be crushed by the disaster he had called upon himself.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Oooh, its a boat."

Qing exclaimed in admiration.

It wasn't as grand as a palace, as Che Nanzheng had claimed.

Still, it was about the size of a 20-person fishing boat. 

It was a certain ship of misfortune one inevitably boarded at least once during a life as a production worker.

But to be fair, it wasn't that bad, even though she was dragged along by her superiors in her previous life.

In fact, Qing only considered the civilization of Zhongyuan to be somewhat above that of primitive people.

Thus, even a boat of this size seemed remarkable to her.

It was like a baby who was praised as a genius for sounding any babble.

'Wow, there's a boat! Wow, a three-story building! Wow, there are carriages!'

'Ancient China is amazing!'

Those were the type of thoughts she always had.

A certain debauchee of Zhongyuan came out to meet Qing.

"Damsel Ximen, thank you for coming."

"It's nothing. I'm here to freeload, after all."

"Haha. Well then. Come. Let me show you around my pride, the Zhaoyang\footnote{lit. 'obvious dick'. The author is messing with us}."

"Ooh. Are you the shipowner?"

"Haha, I hardly ever take the ship out, so it's a bit much to call myself a shipowner. Nevertheless, an owner is still an owner."

Right as she boarded the deck-

\textit{Oh my world! What a sight to behold!}

Qing witnessed a beautiful scene, unrivaled or ever seen before in her life.

A table of drinks and snacks, filled with all kinds of delicacies, was spread out in a T shape.

{\itshape If it was this much hospitality, it could even redeem his Evil Karma of -601 a slight bi-

  What the heck?

  He managed to increase Evil Karma in that short amount of time?}