\chapter{The Waves in Front of the Yangtze River Are Like This and That (7)}

Right then, it became noisy outside, and then the door opened.

A face familiar to Qing stood in front of the door.

It's the bastard who pretended to understand me before fucking trapping me in here!

Qing heightened her vigilance.

After all, she had trusted him because he seemed nice, but look where that got her.

Regardless of what Qing thought though, Bu Penwu, the so-called First Arrival of Yangtze River, spoke his piece with a stern face.

"Young Lady Yun. I apologize, but we need your help."

"So, it has come to this. Didnt I clearly warn you?"

"I have no excuse. If the offer you made before is still valid?"

"For now, let us go."

Qings eyes sparkled.

{\itshape So they're taking this crazy woman, huh?

It was a golden opportunity to escape this wretched prison.

Just hurry up and fuck off. I'm gonna go find my freedom and dip outta here.}

But the antisocial, batshit crazy murder, who was also an Ultra-Supreme Master, was not so easy to deal with.

"And Young Lady Ximen can come along too, yes?"

"No, what? Why me? I'm just gonna stay here, so you two go have a good trip. I'll stay back and watch the house or something."

"Then I won't be able to do anything, would I? Expert Bu, is that truly okay?"

"If Young Lady Yun insists, what else can I do? But, why?"

"Who knows? Perhaps personal reasons?"

Yun Yuanling grabbed Qing, linking arms with her.

Qing's expression soured.

Thus, Qing had no choice but to be dragged onto the deck with her arm taken hostage.

And, lo and behold!

The deck was a sea of blood.

Torn limbs were scattered everywhere.

Various internal organs were also individually displayed, having fallen out of the bodies.

{\itshape Did they seriously have such a merry party without me?

These pieces of shits. Couldn't they have also invited me?

I know how to tear off limbs too, you know?

I want to show off too! Fuck!}

Qing gritted her teeth.

"Oh my. Young Lady Ximen. Are you angry? After mastering such a brutal martial art...Could it be that you were unexpectedly a righteous female? Hehhhhh..?"

"What?"

Yun Yuanling had a massive misunderstanding, but Qing was already far past being disgusted by her. It was literally just as she said. The fuck was she on about, indeed.

Suddenly, Yun Yuanling pulled Qing closer, making her back bend forward. Then, the crazy woman whispered into her ear from a distance that was far too close for comfort.

"By the way. How did you know I was a bad person? That was supposed to be a secret, though?"

"None of your business."

"How cold of you."

Yun Yuanling trailed off as if disappointed.

Qing was absolutely sure this villain didn't feel even a speck of sorrow. In fact, she was willing to bet her entire fortune, no, even her arms and legs on it.

Qing stopped right in the middle of the ship.

The people there were solemnly surrounding something, but they made way for Bu Penwu to enter as soon as he appeared.

And in the center, there was a tightly bound young man.

He was so thoroughly tied up with thick ropes specifically meant for ships that only his head was visible from the veritable bundle.

The young man was trying desperately to say something, but could only manage muffled noises that went, Eup Eup Eup Eup, due to the thick gag in his mouth.

"It is a Throat Jiangshi."

"C-Can he be treated?"

"Half of his Yuan Dan has already been damaged. Even if we break his dantian to release the pressure, he will only have about twenty years left to live."

"Is there really no other way?"

Instead of answering, Yun Yuanling just stared at Bu Xiayun.

But Bu Xiayun merely replied with a pained expression.

"...If the Young Head of the Yun Clan says so, hen that’s all there is to it. Do you need anything?"

"Fortunately, I have most of what I need. My luggage and two fresh hens. And a bundle of eggs. And could you prepare the esophagus for me?"

Yun Yuanling approached the bundle of ropes.

She pressed her index and middle fingers to the young mans forehead and began chanting Daoist recitations.

Surprisingly, she seemed to be quite the capable Daoist Monk.

Thinking that this was her moment to gain information, Qing asked Bu Penwu.

"What exactly is that woman's identity?"

"Have you not heard? She is the Young Head of the Jin Prefecture's Yun Clan."

"I heard that, but so what? What's that supposed to be? What kind of clan is it to produce that kind of thing? She's a complete madwoman."

"Young Lady. I am telling you this because you remind me of my daughter. But even if you come from a prestigious and noble clan from the Orthodox Faction, calling the Wulin Alliances Chief Enforcer such words. Well it is not our place to say such things. If only I had known this would happen..."

Bu Penwu had a complicated expression.

\textit{What the fuck? Why is he playing the victim card when they're the ones who sacrificed me to a crazy murderer?}

Qing ignored his apparent anxiety and pressed for an answer.

"So, what is it?"

"The Yun Clan of the Jin Prefecture are-"

The Yun Clan of the Jin Prefecture were the foremost Daoist Funeral Overseers in Zhongyuan.

Funeral Overseers were Daoists who conducted burials and prayed for the dead.

While monks and Daoists also performed these rituals, only Daoist Funeral Overseers could perform Daoist Magic.

They could animate corpses through this extraordinary Daoist Magic, making them move on their own.

And such animated corpses were called Jiangshi.

"What? Jiangshi?"

"I see you know about Jiangshi."

"Those things that go like this, bouncing around."

Qing stretched out her arms and imitated a Jiangshi.

Bu Penwu clicked his tongue.

"Tsk tsk. That is something only little kids would believe."

"Then just think of me as a little kid. So? What is all this about? What's this talk about a Chief Enforcer? And the Wulin Alliance? That woman is from the Wulin Alliance?"

If it was the Wulin Alliance, it should be a gathering of everyone in the Orthodox Faction. Why would a thing like that be a part of such a group?

Qing glanced at Yun Yuanling, who was writing a Fulu \footnote{Taoist talisman. Most popular depiction in media was to put on corpse's forehead} with chicken blood.

{\itshape Her Evil Karma increased again, huh. When the fuck did that happen?

Am I misunderstanding something?

Is the problem with the Jiangshi? Since she was playing with the dead or something?

No, even if that was the case, there should still be a limit to it, right?

And she herself confessed she was a little cunt, I mean, a bad person.}

While Qing was hesitating over what to think, Bu Penwu began to explain. This man was unexpectedly loose-lipped.

Bu Penwu would have felt wronged if he knew what she was thinking.

After all, he considered Qing a runaway girl from a noble clan of the Orthodox Faction, so from his perspective, it was just a matter of time before she found out.

"Was it about ten days ago? At that time-"

The Chief Enforcer of the Wulin Alliance arrived at the Forts of the Yangtze River Waterway.

And she abruptly stated that several Blood Jiangshi were found in a secret cave nearby.

Creating a single Blood Jiangshi required the sacrifice of no less than one hundred lives.

The Alliance presumed these were the people who had disappeared in the East Sea and concluded they had been transported along the waterways to Dongting Lake.

And there was only one group in the Yangtze River capable of carrying out such a heinous act of smuggling.

It was the Forts of the Yangtze River Waterway.

However, the Wulin Alliance believed that Bu Xiayun's character would never allow for such actions to take place.

And in fact, that was indeed true.

As such, they sent the Chief Enforcer to inform and investigate the real conspiracy.

"The story doesn't add up. And you're switching your words too. You locked me up in a cell, after all."

"We didn't have any other choice but to do that."

Bu Penwu closed his mouth.

After all, from here on out, it was about the affairs of the Waterway Forts.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Forts of the Yangtze River Waterway had changed.

Moving away from being robbers and bandits that rode ships on water, it now resembled a sort of sect with a legitimate business.

Tolls?

In the first place, even Wulin sects collected so-called protection money within their territories.

The champions guarding the Yangtze River collecting a modest toll was quite reasonable compared to them.

However, not everyone was pleased with this change.

For one, there was the Lulin\footnote{lit. 'Green Forest', essentially THE faction of bandits. Regular bandits doesn't dare call themselves a faction}.

As the Lulin and the Waterway Forts had been strong rivals, the evolution of the Waterway Forts was unwelcome to the former.

So, the bandit bastards kept yapping.

'Those embarrassing, ignorant fuckers who don't know their place.'

'How dare they call themselves champions of the people when they're mere dogs of the authorities, feeding off scraps.'

'I would rather cut off my own dick and become a Buddhist nun than associate with the government', etc. 

From Bu Xiayun's perspective, it didn't matter what the bandits said.

No, the problem was that members of the Waterway Forts started agreeing with them.

They were the so-called traditionalists, led by the previous generations demonic humans.

Human trash that couldn't forget the taste of looting, raping, and cannibalism. And those who joined the Waterway Forts hoping to become future pieces of shits supported them.

Moreover, since the bastards were clearly scheming something, when he heard the words Blood Jiangshi, it made him veritably dizzy. In fact, he almost fainted in anger and shock.

The traditionalists weren't plotting something simple. It was far from ordinary.

As such, if mishandled, the entire Waterway Forts could be utterly destroyed.

This matter had to be dealt with internally!

It was the time to show that they could avert such a crisis and say, 'We had this and that happen, but fortunately, we were able to prevent it on our own.'

That was the reason for detaining the Wulin Alliance's Chief Enforcer.

The Fort Commander, Bu Xiayun, looked at his son and thought.

\textit{However, even if it meant facing further interference, perhaps we should have accepted the help of the Wulin Alliance. Then, maybe that child too-}

It was right then that it happened.

"Hooo."

Yun Yuanling sighed deeply, wiping sweat from her brow.

"What happened? How did it go? The child-"

"Fortunately, it went well. He shall regain consciousness soon."

Bu Xiayun exhaled deeply.

It was better than dying, even if his lifespan was shortened.

"Did you say about twenty years?"

"The treatment went well, so he will live a bit longer than that."

Bu Xiayun thought that that was enough.

Now, he just needed to quickly arrange a marriage for his son and hope for the best.

Bu Xiayun clasped his palm around his fist in sincere thanks.

"I, Bu Xiayun, will express my gratitude to the Benefactor."

"Benefactor? Not at all."

"No. You saved my child's life. There is no greater benefactor in the world than you. What else could I possibly call you?"

"I'm really not, though..."

Yun Yuanling answered with a strange smile.

It was a smile that seemed somewhat inscrutable. But without a doubt, something was off. Perhaps even suspicious.

However, Bu Xiayun was in a dire situation, akin to having fire set below his feet.

Moreover, it was a spark that, if not shaken off, could spread all over his body.

His urgent thoughts brushed aside his capacity for critical thinking and deeper contemplation to the signs given.

The reason was simple; above all, she had saved his son.

However, the situation was still far from ordinary. In fact, it was incredibly severe.

The arm of the Regional Inspector had been severed and the perpetrator was none other than the Waterway Fort Commanders son, Bu Qianzhi.

Moreover, he had loudly claimed that the attack was ordered by Bu Xiayun himself. None of the soldiers who managed to escape with the Regional Inspector could have missed hearing those words.

\textit{What am I supposed to do about this?}

Right then, Bu Qianzhi awoke.

"Ugh. My head..."

As Bu Qianzhi pressed at his temples, he abruptly trembled.

He looked around in shock and then urgently called out to his father.

"Father! W-We're in huge trouble! It is a disaster! The main house, the main house is overrun with those damned bastards! Those cursed demons! The family of the Waterway Forts are! "

Qing watched the scene unfold with a blank stare.

The situation seemed kinda serious.

And people were scurrying about, talking of turning the ship around and rushing to save the main house or something.

Amidst the bustling crowd, Qing stood alone.

And that was when she suddenly came to her senses.

This isn't the time to just stand around and watch.

\textit{I gotta dip before that woman latches onto me again.}

"Oh my. Where do you think you are going?"

A chill ran down her spine for a moment.

Yun Yuanling had somehow appeared beside her without her noticing.

\textit{Motherfucking piece of shit. What a damned, fucking bitch.}

Qing, who genuinely shivered in disgust, quickly turned utterly solemn. 

But it didn't seem like Yun Yuanling gave a single flying fuck what Qing thought or how Qing reacted. 

She just leaned in close to her ear and whispered in a soft voice.

"It will begin very soon. But still, all you need to do is stay calm. I will protect you. After all, Young Lady Ximen, you are far too frail, insignificant, and pitiful."

Qing grimaced.

It wasn't because her pride was hurt that an Ultra-Supreme Master called her weak.

Compared to that monster, it was probably true anyway.

It was just because of the unwanted Mission Window that popped up before her.

\textit{Fuck. Seriously, fuck. Fuck, fuck, fuck. Fucking hell. FUCK.}