\chapter{The Waves in Front of the Yangtze River Are Like This and That (9)}

In normal cultures, cannibalism was taboo.

And even if this was ancient China, such a cultural value remained identical.

It was so taboo, in fact, that one of the greatest punishments was to kill a criminal and feed their flesh to their family.

However, there was no culture that did not practice cannibalism.

After all, when people were too hungry and they had to choose between survival and dignity, they would almost always choose the former.

However, it was a shameful act.

Too shameful to even speak of.

But even among them, there were some bastards who knew no shame.

The Demonic Cannibal was that very bastard.

Among people, there were occasionally those who, despite no one else doing so, acted in such a way by themselves to somehow prove their superiority. Whatever the fuck that meant.

Leaving aside nutritious and delicious dishes, he would stubbornly eat the rotten and tough meat of humans.

'I can do what you cannot do.'

'And that makes me superior.'

Driven solely by a twisted desire for recognition that he was superior to others, the Demonic Cannibal reached the Late-Stage Transcendent Realm.

And to become even more superior, he even mastered cursed Demonic Arts.

Soon, the world would face an even more vicious villain, the Flame Demon.

But then, someone directly challenged the authority he had built up with blood and resentment.

Moreover, it was the youthful voice of a bratty girl, clearly still wet behind her ears.

It was a move that truly touched upon his reverse scale.

The Demonic Cannibal lost all sense of rhyme and reason.

"WHICH BITCH! DARES!"

"Master!" "Oh, Demonic Cannibal!" "You cannot! The ambush-".

His subordinates didn't even have a chance to stop him.

With his beard turned bright red with Demonic Arts, he stomped fiercely off the ground and leapt forward.

All that was left was the deeply indented floor.

The subordinates helplessly waved his hand that he had raised in vain.

An ambush has been prepared.

Memories of the hardships he had suffered flashed through the subordinates mind.

Those days he dug the ground, hid Jiangshis among the family, practiced retreats and counterattacks according to regions, and rolled around, yelling the slogan of total annihilation.

The subordinate shook his head and gave the order.

"What are the rest of you doing! The Demonic Cannibal himself has taken the lead!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After the rough landing, Bu Xiayun, who was driving the river bandits back towards the main house, heard that outrageous provocation.

It was a curse so disgraceful that one would hesitate to even think about uttering. In fact, it was so severe that one wouldn't even say it to their worst enemy. But regardless of that, the true problem was who it targeted.

\textit{The Demonic Cannibal, she said? Why would the Demonic Cannibal come out here?}

But then, the firmly shut gates of the main house were blasted open with a roar.

It was truly an overwhelming presence.

The advance of the Waterway Forts stopped hesitantly.

A figure of astonishing stature, both vertically and horizontally, revealed himself.

A red aura swirled around.

The killing intent had become so tangible that it had reached a realm where it could be seen.

It was a stage where ones Inner Qi moved on its own accord as their mind worsened.

It was all too clear who it was.

"Demonic Cannibal!"

Bu Xiayun shouted as if to scream.

And in reality, it was indeed close to an actual screech.

He couldn't even confront him, asking why someone like him was here. After all, they could not hope to face a wicked Demonic Adept at the Late-Stage Transcendent Realm.

"WHICH BITCH! DARES! DARESSS! I WILL NOT KILL YOU EASILY! I WILL EXTERMINATE YOUR ENTIRE LINEAGE, SALT THEIR FLESH, AND FEED YOU UNTIL YOUR STOMACH BURSTS!"

"You really love to eat, huh! Damn, just stop eating! Your stomach is about to burst! Literally! "

With a mocking laugh, a figure in blue dropped down among the river bandits and the Demonic Cannibal. 

"Hello there, Senior! This lowly student of Wulin, Ximen Qing, greets you with all her heart!"

"YOU, YOUUUU!"

"Calm down! You're going to keel over from high blood pressure before we even get a chance to fight! What are you doing?! Come at me! \textit{Hwaiting}!\footnote{Cheer to pumping up oneself or others}"

"GAL!"

{\itshape 'Gal!' has made its entrance!

So it wasn't just something that came up in funny posts!}

Qing swallowed her admiration.

The Demonic Cannibal's log-like foot lifted.

Qing shouted.

"WAITTTTTT!"

It was a perfect instant to catch him off guard, causing the Demonic Cannibal to momentarily falter.

It was then that it happened.

Chak Chak Chak Chak Chak. The sound of five light landings.

Behind Qing, five children appeared.

"AGAIN, HERE WE GO! MY! MOONLIGHT SWORDDDDDDD!"

Qing charged with renewed courage.    

The Demonic Cannibal, mixed with feelings of anger and puzzlement, rapidly closed in.

\textit{The presences felt from behind was definitely reassuring, though.}

Qing raised her sword cheerfully.

A pseudo-martial artists fraudulently accumulated Inner Qi flowed into the sword as a solemn stream.

The doubly-powered knowledge of Zhu Xiangs Heart Cleanse Mirror turned the Sword Qi into a sunset hue, leaving a long vertical afterimage as it fell.

The Pressure of Mount Tai. The oppressive feeling that seemed as if Mount Tai itself was bearing down.

It was the only move that her teacher had somewhat praised for having even the slightest bit of Imagery. In other words, she was basically calling Qing a one-trick pony.

But still, the Demonic Cannibal's hand was dyed blood-red.

\textit{A mere Late-Stage Peak Realm brat dares!}

Sword Qi and Hand Force clashed.

Clang! The sound of their collision was unbelievably loud.

Qing, unable to overcome the difference in weight class, was sent flying.

The Demonic Cannibal's hefty body leaped, following her trajectory.

Qing quickly flipped her body around.

The ultimate fatty approached right in front of her. His blood-red hand rose.

Qing stretched her hand far behind her waist.

But the difference in their realms was all too clear.

The Demonic Cannibal's hand began to fall first.

Suddenly, Taaang!

Three children leaped up and blocked the Demonic Cannibal's strike.

Qing had never intended to solely rely on her own abilities in the first place.

"I believed! It was there!"

Qing pushed her sword forward.

A thrust filled with brute force, without any fancy techniques.

The sword, moving at the speed of light, aimed for the Demonic Cannibal's hea-

In an instant, the Cannibal's hand grabbed the blade.

"What a pity, brat. If it wasn't for my Divine Arts, it might have worked."

There was a Wulin custom among those who possessed Demonic Arts; even in death, they would not openly admit to using Demonic Arts. 

When the Demonic Cannibal mentioned Divine Arts, he naturally referred to the Flame Demonic Arts.

Qing didn't know anything anyway, but the Flame Demonic Arts originated from the White Hand Demonic Arts.

Originally, it was a complex concept, but when simplified, it was based on the inversion of Yin and Yang, so it's effects were somewhat similar as well.

For example, he was able to refine the body parts below the elbow. 

When adding the Late-Stage Transcendent Realm with the completion of Eight Stars in the Flame Demonic Arts, a blade surrounded by Sword Qi was no better than a club.

Such was what made the renowned Demonic Arts so fear-inducing.

And it was also the reason why people dared to master it despite the risk of becoming a public enemy of Wulin.

"Ah. So this doesn't work, huh."

The Demonic Cannibal pulled Qings sword towards him.

His other arm was already loaded with the Flame Hands.

A true swordsman would rather die than let go of their sword!

Qing let go of her sword without hesitation.

\textit{Well, I guess I just won't be a swordsman anymore.}

The Cannibal's eyes flashed.

He planned to deal with the annoying young ones first while the girl had stepped back in retreat.

His hand, filled with Toxic Flame Demonic Qi, smacked down on one of them with the expectation that their flesh would explode into pieces, but-

Clang! With a sound like striking iron, the child was sent flying and bounced off the ground about five times before falling far away.

The Demonic Cannibal was shocked. 

\textit{That's a Jiangshi! Why?!}

The Cannibal's eyes darted around.

And then, he spotted Yun Yuanling among the river bandits.

-What is the meaning of this?! Why is a Jiangshi attacking me?!

It was an art, a skill used by very advanced Masters.

A technique that forcefully projected sound into the counterpart's ear through a soft whisper protected by Qi that was only rolled in one's mouth. 

It was a method used for secret conversations when needed.

This technique was called Sound Transmission.

Yun Yuanling's own Sound Transmission came flying through.

-Strictly speaking, it is not an attack. The children are just protecting Young Lady Ximen.

-How does that make any sense?! Why would you protect someone like that brat?! I could rip her apart like the wretch that she is and I still wouldn't be satisfied!

-Ah. That is my personal affairs, you see? And we are not exactly in a position to share personal affairs, are we?

-Ha, you bitch. Do you think you can get away with breaking the Associations rules just because you are favored by the Association Leader for your ability to create Jiangshi?

-Who knows.

Yun Yuanling merely showed a troubled smile, as if her hands were tied.

To her, changing out the Association Leader was not an issue at all. He was kept around because he was easy to manipulate due to this stupidity and greed.

Yun Yuanling sent another Sound Transmission, hiding her mocking scoff.

-Young Lady Ximen is quite stubborn, you see. Could you just engage with her until she runs out of energy? You have the capability to do that much, dont you?

-What sort of dogshit is th- Keuk.

The Demonic Cannibal was about to respond, but had to urgently spread his hands.

It was because Qing had charged at him again.

Qing, too, had picked up a few things, so she charged in while believing in Guanxi, just like the people of Zhongyuan. But despite her belief in Yun Yuanling's protection, he was not an easy opponent.

Moreover, the Jiangshis only defended.

She had to land the fatal hit herself, but due to the difference in their realms, that was also easier said than done.

\textit{Teacher, what should this disciple do?}

Qing recalled a conversation she had with her teacher.

'Master, what if an enemy is like an Ultra-Supreme Master?'

'Then you must run away immediately. What else could you possibly do?'

'What if I can't run?'

'If you must face such a formidable opponent-'

Wear them down.

Once the dantian was drained, it didn't matter if they were at the Transcendent Realm or the Fatscendent Realm. She just needed to endure and endure until all his Inner Qi was depleted.

Of course, it was impossible in a one-on-one situation.

After all, the Inner Qi of a Master was far greater and even more efficiently used, so there would never be a case where a Master's dantian would deplete first in normal circumstances.

'Then?'

'There is something Disciple is good at, isn't there?'

'Something I'm good at?'

'I am referring to how you make this Teacher's stomach turn in anger at times.'

Make the opponents stomach turn in anger.

'Your unique technique could practically be called a Divine Art, unmatched in all under the Heavens. If you can infuriate the enemy, erase their rationality, and dodge well, there might be a chance for victory.'

That was indeed Qings area of expertise.

But deliberately doing so felt strangely embarrassing.

It's a bit hard to shout these things out loud while completely sober.

It was just like how it was easier to sing with a bit of alcohol.

The bullshit Qing spouted followed the same principle.

It came out well when angry or a bit disoriented.

If not that, then when she was excited.

She needed that sensation when she was covered in blood, pulling out intestines to wear around her neck. And breaking bones to feel the crunch.    

Only then did true excitement surge and a genuine sound came from the very depth of her dantian.

But now that she had to speak with a level-headed mind for the sake of victory, she felt slightly apologetic.

And it felt a bit embarrassing to talk when others were listening.

So, Qing spoke just loud enough for the Demonic Cannibal to hear.

To others, it might have seemed brave for her to charge in despite the difference in their realms.

However the actual sounds that popped up whenever she clashed and dodged; the true words that could only be heard up-close were as follows.

"Hey. You fucking pig. I heard you called yourself the Demonic Cannibal, yeah? Holy fucking shit, how much do you have to eat to look like that? Tell me honestly. It kinda seems like your chest is bigger than mine, you know?"

The Demonic Cannibal counted Buddhas in his mind.

{\itshape The bitch that creates Jiangshi is a key talent to the Association.

And without Jiangshi, the grand undertaking was impossible in the first place.

Since it is such a bitch's request-}

"Hey, but if you're a cannibal, you eat in all types of ways, right? Boiled, roasted, steamed, and the like. If that's the case, when you take a bath, do you drink the bathwater? It must be like brewing a rich broth, huh."

"..."

"Woah, honestly, I'll admit it. You're impressive. If I was hearing such nonsense, I really wouldn't have just stayed quiet. Do you have some kind of hobby of getting insulted? Maybe a masochist? Are you not mad even though I'm provoking you like this? Should I shit on your family once?"

"..."

"Do you know the principle of how like cures like? You know, when you're hurt somewhere, you just need to eat that body part to feel better. So if your eyesight is bad, then you eat eye dishes. If your liver is bad, you eat liver. Then, doesn't that mean you eat people because you aren't human enough?"

"..."

"If that's the case, from now on, you should eat more elderly people. Since you don't have your mommy and daddy, you should consume other mommies and daddies to-"

"EUAAAAAAAAAAAGH!! I WILL KILL YOU!!! I WILL KILL YOU NO MATTER WHAT!!!"

Finally, the Demonic Cannibal exploded.