\chapter{Are You Acquainted With This Beggar? (14)}

Qing, officially visiting Changyuan City for the first time, was surprised.

It's a natural phenomenon for the gender ratio to be skewed when the Jade Qilin appears.

\textit{Although the numbers had decreased somewhat-}

\textit{Even after that commotion yesterday, they only decreased a bit, where on earth does this obsession come from?}

\textit{Moreover, what's this, why is everyone like that?}

Qing tilted her head.

It was a strangely noticeable sight.

Oddly, two out of three women were dressed in dirty clothes covered in grime, with their hair disheveled like beggars.

Their clothes were those of beggars, but their faces were heavily made up with powder and lipstick.

It was as if some bizarre end-of-century trend had finally arrived in Zhongyuan.

This beggar trend arose because yesterday, the Jade Qilin declared that dirty beggar women were his type.

In Zhongyuan, trends are called '\~feng' (wind).

The common expression 'a gust of wind is blowing' originated from this.

"People with perfectly good limbs pretending to be beggars? Just to look good to a man? Really now."

This was Qing's (the beggar's) cold assessment.

Seeing this crowd of non-beggar beggars, she could somewhat understand Peng Daesan's woman-hating trembling.

In fact, given the era, even if women behaved like this, it was packaged nicely as pure love due to romantic feelings, making it even more extreme.

Qing had only heard that the Peng Clan of Hebei had unpacked at the Changyuan Daoist Temple, but not where the Changyuan Daoist Temple was.

However, she didn't need a guide.

She gracefully walked towards where many alleged female beggars were visible, and gradually the surroundings were filled with alleged female beggars.

Finally, one street was full of female beggars, swirling in a large circle as if cursed by a whirlpool.

In the middle of this beggar scene, a gate stood tall with a heavy, imposing sign that read ""Changyuan Daoist Temple'.

As Qing headed towards the gate, the women's hostile gazes stabbed at her.

However, Qing was already a Jade Qilin expert.

She was used to this terrifying hostility.

Rather, she pushed out her chest, which was already protruding at a false start level, and straightened her shoulders even more. 

\textit{What's this, why does it feel good?}

\textit{What's with this pride, put it away.}

Qing was momentarily confused.

The gate guard of the Changyuan Daoist Temple also seemed confused, standing at the gate with his mouth open like an idiot expecting a fly to fly in as he saw Qing.

"……"

"Sir guard?"

"Ha, does the young lady have business at the Changyuan Daoist Temple? If you're visiting, please write your name in this guest book, and I'll report it inside."

"I'm Ximen Qing, an outer disciple of the Divine Maiden Sect. Wasn't there a message in advance?"

"Ah, Miss Ximen! We heard you were visiting today!"

As Qing entered the Changyuan Daoist Temple and walked in, she saw a familiar figure in the distance.

Since she had never seen anyone else that tall in Zhongyuan, it could only be Peng Chaolei.

"Oh, isn't it Qing'er! Wow, I saw you from afar and it suddenly became bright and dazzling, so it must be Qing'er. Such a beneficial beauty. We heard in advance that you were coming today."

"Miss Peng, have you been well?"

"Oh my, you've become a complete heavenly woman?"

At this, Qing broke her beauty act and flashed a mischievous smile.

"Hehe. It doesn't suit me, right?"

"No. Even as a fellow woman, I almost lost my senses. I thought you were the rough type like me, but that's not it?"

"That's right. But my master is strict."

"Ah, the Grand Matron! But, Qing'er? Miss Peng? Are you going to be so stiff and formal with the Peng miss who's listening? There's a word called ‘Jiejie' (older sister)."

"Uh. It feels really awkward. It doesn't stick to my mouth."

'Sister' was really too much.

She had called her sworn sister 'Sister' just once because she was so upset, but the moment it left her mouth, goosebumps rose all over her body, indicating a more fundamental, some kind of physiological fear.

Qing's expression was more effective than a hundred words, so Peng Chaolei, who read (or rather, just saw) that reluctant look, changed her words.

"If it doesn't stick to your mouth, just call me Chaolei by name. Miss Peng is too stiff between us. Come on, try it, Chaolei."

"Yes, Chaolei. I understand."

"By the way, where did you put the great sword I gave you and picked up that thin, long blade?"

"Well, it was too heavy and big, so I left it behind. The sworn sister who's going to serve me this time is weak, so I felt a bit sorry to entrust it to her."

"Great swords are all good, but they do have that minor problem."

In fact, Peng Chaolei herself was wearing a thin short sword at her waist, so the very minor problem of the great sword's portability was too minor.

"Ah, Qing'er, I heard the story. Oh my, our good Qing'er has been through a lot."

"What? Did San spill everything?"

"What could I do when he asked me for help?"

Peng Chaolei added an explanation.

Apparently concerned about the rumors, Peng Chaolei said she would pretend to be a flower beggar and walk around with her brother today, so Qing should join them.

"Father doesn't know, so please pretend not to know otherwise. He's a bit angry at my brother, but if we leave it for a few days, he'll act like it never happened. Ah, but then, you two were together yesterday, right?"

Peng Chaolei's eyes lit up.

It seems Chaolei was misunderstanding the relationship between San and me.

Qing answered with a smirk.

"Chaolei, San and I are just friends. If I had any feelings to begin with, would San have tolerated it? He would have chased me away, lowering his voice and going ‘grrrr'. I remain San's only female friend because it's a pure friendship."

"Hmm."

"So, I was thinking, how about throwing a party to celebrate San losing his virginity? Don't you think his expression would be totally sour?"

Looking at the eyes sparkling with pure desire to tease, Peng Chaolei muttered.

"Ha, this kid. Your path of hardship is clear……"

"Well, I won't tease him enough to call it hardship……"

"No. Being this pretty. That stupid bastard. That party might be okay at our clan, but it's a bit much at someone else's house. Come visit the Peng Clan next year. Let's tease him grandly with a first anniversary celebration. How about it?"

"Hmm. Since a day has already passed anyway, it's fine to look forward to next year."

"Right? Is it a promise? You must come, okay? It's April 21st, so a week before, yes, come by April 15th at the latest."

"Yes, Chaolei. April 15th."

Peng Chaolei very skillfully set up the promise.

Qing nodded in agreement, not realizing she had fallen into a trap.

And then, to greet Peng Clan Leader Peng Xian, hmm? Is that right? Shouldn't it be the Changyuan Daoist Temple leader first?

As Qing got confused, Peng Chaolei explained that since she came as a guest of the Peng Clan, it was natural to greet the Peng Clan Leader first.

The Daoist Gentleman Peng Xian was a very generous person.

"Child!! Yes, welcome! I've heard a lot about you from our little sparrow. Seeing your face like this is truly wonderful!"

"Father, how old am I for you to still call me little sparrow? And in front of a guest at that."

"Haha, in a father's eyes, you're always as small and cute as a little sparrow, no, cuter than a sparrow. Isn't that nice!"

Qing was confused.

\textit{Isn't that sparrow the same sparrow?}

\textit{Are sparrows in Zhongyuan as big as eagles?}

Qing, who didn't know about Peng Chaolei's childhood when she was only as big as a palm, could only wonder if that sparrow was a different sparrow.

"Sigh, I'm ashamed in front of you because my son caused trouble. He usually doesn't listen, but I really don't know what he's thinking. That boy is always gloomy."

"Ah. I think I understand that. Ah, do you have a different nickname for San too?"

Qing's eyes lit up, thinking she might be able to gather some teasing material.

But it was a dud.

"San! That's nice! But, that boy doesn't have anything cute about him to give a nickname. He just twitches his eyebrows when you say something. Aish."

"Heheh. I understand what you mean."

"You truly overflow with dignity, child. Our family tradition is rarely so free, but seeing you like this, yes, it's good! I like it!"

\textit{I'm not sure what exactly he keeps liking, but I can tell he's welcoming me heartily.}

After that, she had a brief conversation with the Changyuan Daoist Temple leader and then immediately prepared for a walk.

Peng Chaolei stuffed cotton cloth into her chest to create a large shape and put on a face veil.

While Qing was just thinking 'Was I that magnificent?', Peng Daesan was nodding very satisfactorily.

"What, San. Was I… that figure?"

"Sister is about an inch taller, but anyway, when you stand and walk around, if your chest is big, doesn't your figure flow downwards? Sister, could you hunch your shoulders a little? Hmm, it's perfect."

Indeed, when she hunched her broad shoulders, she looked almost like the flower beggar.

Of course, since the only characteristics were the face veil, height, and chest, it was natural.

"After we go around a couple of times, we'll part ways and you'll leave the city, then the nasty rumors will end too. We need a lot of onlookers to follow us."

"Huh? San. Haven't you been outside? The whole city is full of beggars. Women have set up camp in beggar outfits trying to catch your eye."

"…? They stayed even after seeing that scene yesterday? Just how much more shameful behavior do I need to show to make them lose interest?"

It was natural for Peng Daesan to be surprised.

Qing, who had nothing else to say, just comforted him.

"Hang in there. I didn't know they were this persistent."

"Damn it. I'm going crazy."

Then Qing snapped her middle finger.

"Then, let's see how far they'll follow us like dogs."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As soon as the three of them left the Changyuan Daoist Temple, pitiful exclamations burst out all at once.

The Jade Qilin came out with women on both sides.

On one side was the peerless beauty who had entered about a shichen ago, but she was walking at a distance, while the one clinging closely and creating a couple's atmosphere by linking arms affectionately was that female beggar from yesterday.

While there was relief that the peerless beauty seemed to have been rejected, what on earth was that beggar woman doing?

The sound of teeth grinding, abbreviated as adeuk badeuk, followed the sighs, making one's teeth ache just from hearing it.

And then, as if to show off, they strolled around the city closely together.

Women with eyes like axe blades followed behind in a swarm like an angry mob filled with resentment.

After they had gone around roughly one lap like this, it happened.

"Young Master Peng! How, how could you do this! How……"

A woman blocked the way and poured out her resentment with tears in her eyes.

But her beauty was extraordinary.

With a face as small as a fist and features packed neatly into it, it was surprisingly beautiful to the point of being strange.

With her tall, slender body and teary eyes, her appearance of sniffling was that of a delicate, sad beauty.

"Miss Murong. You speak as if I have caused you some offense. We are simply lovers taking a stroll, so would you please step aside?"

Qing reflexively looked at Miss Murong's chest.

\textit{What? There's quite a presence there, isn't there?}

A-Jun said he only had one sister.

With beauty like that, she seems to fit the Five Flowers of Zhongyuan.

"Ah, no! You can't! How can you walk with women on both sides, leaving me behind! It's too much! What part of me is lacking!"

"If others hear, they might misunderstand. Miss Murong and I didn't have any particular relationship, did we?"

"How, how can you say such things…! Rather than that beauty beside you, how can you be with that dirty beggar woman, she's even an ugly bitch!"

-No, she's. No matter what, to point and curse at someone's face like that. I didn't think she was like that.

This was Peng Chaolei muttering.

Unaware that her reputation was being severely damaged in the eyes of everyone's big sister Peng Chaolei, Murong Zhuxi threw a tantrum.

At that moment, when Qing cleared her throat ahem ahem, Peng Daesan, whose voice had been gradually lowering in pitch, flashed his eyes.

"Hmm. Come to think of it, Miss Murong's words seem right. I like the dirty part, but she's just tall as a pole. Besides her night skills, there's nothing else I like about her. Ha!"

With that, Peng Daesan shook off his arm, and Peng Chaolei, with her all-out acting performance, tumbled and fell pitifully to the ground with a thud.

"Y-young master? How, didn't you promise to cherish me for life?"

"Know your place. Did you think a lowly bitch like you could set foot in the great Peng Clan of Hebei?"

"How, me, hic. Now that you've had your way with me, you're saying you don't need me anymore? After using my body so beastly last night, how…"

"Isn't that how men are? Come to think of it, if I like the beggar look, I could just dress up a pretty girl, there's no reason to associate with a real beggar woman. And with that ugly face, thanks to which I even skipped breakfast, cover up that disgusting face and get lost."

"That! Indeed! I understand! This damn sleeve, here! I've torn it all off!"

Peng Chaolei grabbed her own shoulder blade and ripped it off, revealing Peng Chaolei's muscular arm with clearly defined muscles by region.

"You said sleeveless clothes were pretty, but this girl was too shy to follow! But for you, young master, I can do anything-"

"Ha, half the world is women, what difference would dressing up make for the likes of you. Enough, get lost. Quickly."

At this, Peng Chaolei put on a crying act and jumped up to run away.

The women in her path were hit by her muscular shoulder and almost flew away.

It was like a flower beggar's cavalry charge rundown.