\chapter{Are You Acquainted With This Beggar? (9)}

Meanwhile, there was another person burning with anger besides the Black Store Leader.

"These parasites who only suck the blood of civilians, who should be hiding quietly under rocks to avoid being seen. How dare they put a bounty on my disciple? I should have exterminated them and wiped out their seed long ago."

Blue flames shot up from Ximen Surin's eyes.

This is not a metaphorical expression.

It was an actual eruption of Inner Qi, and because it was the color of the setting sun from the Zhu Xiang Heart Cleanse Mirror, it flickered like flames.

It was the master's anger after hearing the circumstances.

Moreover, it was even more so because her disciple had done absolutely nothing wrong, not even a speck.

She was a disciple who raided an unorthodox faction and tracked down and dealt with slave traders to help one innocent old man.

While she could be scolded for being careless and reckless in her behavior, it was truly a righteous deed that would make her name widely known as a female martial artist and chivalrous hero.

She was a disciple who deserved praise a hundred times over.

But what? Ten thousand gwan of gold?

Although her disciple had cleverly hidden her name, it would eventually be revealed anyway.

Ximen Surin rose from her seat.

"It's been a while since I've seen Cao Xuanliang's face."

Cao Xuanliang\footnote{曹玄亮. The 曹/Cao character is the same as used in Cao Cao's (曹操) name. Jo Hyeonryang (조현량) in the original text} is the Grand Patriarch of the Black Dragon Cao Clan, one of the Nine Great Clans, no, the Eight Great Clans after the Jin Prefecture Yun Clan was destroyed and its only successor defected.

He was more famous by his name as the current Wulin Alliance Leader.

Originally, she wasn't going to participate in the Wulin Conference.

It was her disciple who should shine in that place, not Ximen Surin herself, so she had intended to avoid it on purpose.

Ximen Surin, sortie.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was an important agenda for this Wulin Conference.

A vacancy had occurred in the Ten Great Clans with the Jin Prefecture Yun Clan dropping out.

The Jin Prefecture Yun Clan had been destroyed, or more precisely, it had been burned from within by a defector.

Murong Chengyi\footnote{慕容成益. Moyong Seong-ig (모용성익) in the original text}, the clan leader of the Murong Clan, muttered.

"A-Ling, that child wasn't the type to do such a thing."

Yun Yuanling was originally betrothed in the womb between the Yun Clan and the Murong Clan, so when she was little, she came to cool Liaoning every summer for vacation.

The little Yun Yuanling that Murong Chengyi had seen was a sickly and weak-hearted crybaby, but he hadn't seen her since the Jin Prefecture Yun Clan suddenly and unilaterally broke off the engagement.

He only occasionally heard rumors that she was doing well as a Wulin Alliance patroller.

What on earth happened to make her like that?

However, it would have been quite chilling if the marriage arrangement hadn't been broken off.

It might not have been the Jin Prefecture Yun Clan that was destroyed.

Who knows, maybe the child harbored resentment after experiencing something after the broken engagement.

She was a timid child who trembled in fear at the sight of any beast or bird, even cute animals like martens or squirrels that normal girls would find adorable.

It was incomprehensible how such a child could harbor resentment and annihilate her clan.

Anyway, since hearing that news, he couldn't help but become sensitive about his children's marriage prospects.

So he had to react sensitively to the news brought by Guard Bai.

‘Clan Leader, these days the young master is associating with a beggar. Moreover, there are bizarre rumors that she's a terrible harlot. What should we do about this? Is it only during the day? Guard Lu doesn't stop him at all at night, so they're on the verge of developing feelings seeing each other every night. We must immediately capture that bitch- no, that woman, beat her, sternly scold her for her advances, and drive her away!'

However, the story written by Guard Bai in sign language was contradictory to this.

\begin{quote}
「Although her behavior appears to be that of a beggar. Her words are reasonable and logical, and she seems to be a wise woman.

Moreover, in dealing with the young master, she treats him only with the attitude of an older sister, and the young master also follows her as an older sister, so it's nonsensical slander to discuss matters between men and women.

Furthermore, her martial arts are powerful, with at least Late Stage Peak Realm capabilities, so she teaches the young master every night, and the young master has shown great achievement recently.」
\end{quote}

In fact, Guard Bai was frustrated because he couldn't find fault with everything being crooked.

The words of Guard Lu, who was taciturn (because he was mute) and earnest, and who volunteered for the arduous night guard duty, were much more believable.

But both testimonies ultimately pointed to a beggar.

With the clan's prestige, how could the direct legitimate heir associate with a female beggar, not even a member of the Beggar's Union?

Moreover, Guard Lu was single, and Guard Bai had two wives.

Guard Lu didn't understand matters between men and women, so he didn't know the principle of sisters becoming ladies and ladies becoming wives.

Just recently, Murong Chengyi had his son's wet nurse snatched away by his younger brother.

After pondering what to do, Murong Chengyi decided to hear the story from the person himself.

Of course, from the son's side, not the beggar's.

"Jun'er, I hear you've been associating with an unusual friend lately?"

"Ah. You mean beggar sister?"

"Hmm."

He was already at a loss for words.

\textit{If she's a beggar, she's a beggar, and if she's a sister, she's a sister, but what on earth is a beggar sister? How can the word sister even follow beggar?}

Moreover, these words were coming from the mouth of the direct descendant of the great Murong Clan.

"Yes. How did you come to know this acquaintance?"

"She's not an acquaintance, she's a friend!"

"Hmm."

\textit{It's already progressed to friends, he says.}

Murong Chengyi's expression became even more serious.

"You know, father. Before, Warrior Bai said something, that female beggars are all dirty, umm."

"Why did you stop?"

"Beggar sister said we shouldn't use bad words, so it's a bad word. She said we should be especially careful in front of our parents."

"I'll specially allow it just this once. So?"

"He said all female beggars are dirty whores…"

"That bastard Guard Bai…!"

A vein popped out on Murong Chengyi's forehead.

"It is a bad word, right…?"

"Yes. You shouldn't use such words carelessly. Not just in front of your father, but when talking to anyone, using such words only degrades your dignity, so you shouldn't use such terms."

"Ah. Beggar sister said that too. She said using bad words is like shouting that I'm a bad person, so it's better not to use them at all."

"Hmm."

Murong Chengyi's expression softened a bit.

\textit{Guard Lu's written message said her words were reasonable and logical, and she seemed to be a wise woman.}

\textit{As expected, Guard Lu is more trustworthy.}

"Hmm. And? Did you learn anything else?"

"Ah. And…"

Murong Jun excitedly recounted Qing's gender equality education to his father.

Although it seemed too favorable to women in Murong Chengyi's ears, it was a valid education about proper behavior, speech, and mindset.

Since a woman taught it, it was favorable to women, and even then, it was virtues that men should rightfully uphold, so there was no problem.

It's just that everyone knows but doesn't follow.

"What do you think, father? Is it all correct? Beggar sister said that when I hear unfamiliar stories, I shouldn't try to understand them alone but should check with adults…"

"Excellent. Everything you said is correct."

Murong Chengyi smiled broadly and opened his arms.

Excited, Murong Jun jumped into his father's embrace.

But Murong Chengyi's heart was not excited.

Rather, it felt like a heavy boulder was tied to it.

Hearing the story about trying to buy breasts from a beggar woman with a gold sycee made him feel like he was falling from a thousand-foot cliff.

Moreover, 'when I hear unfamiliar stories', he says.

Everyone was excited about teaching martial arts to the youngest son born with the Heavenly Martial Body.

Not a single person until now had taught him these obvious principles of human conduct that should naturally be followed.

Even Murong Chengyi was the same, thinking it was so obvious that he would naturally know, or that he would understand when he grew up.

\textit{Come to think of it, how could one understand without being taught?}

\textit{Usually, the mother should step in to admonish, but ah, wife, why did you leave so early…}

\textit{I looked down on her because she was a beggar woman, but it turns out she was my son's benefactor!}

\textit{I was taught to regard everyone I meet in the world as a teacher, but I've become thick-headed and acted like this!}

\textit{I should immediately call that woman and express great gratitude…}

"…And, and. Right! Beggar sister asked me to marry her."

"What? How dare she- so, how did you answer?"

"I said I don't like women who cover their faces. Father, you said so, didn't you? That women who cover their faces do so because they're horrible to look at…"

"Yes. I did say that. Phew. Well done. You did well."

Murong Chengyi was greatly thankful for his own teaching that he couldn't even remember.

\textit{Now I see she wasn't the child's benefactor but a schemer with a black heart!}

\textit{It was a ploy to seduce an innocent child and try to change her fate!}

"Jun'er, father is saying this just in case, but marriage is a major family matter, so you absolutely, absolutely must not decide on your own. And especially not with that beggar woman. Absolutely not. It can't happen even if dirt enters this father's eyes."

"I said I didn't want to either. So beggar sister said she would absolutely never marry me no matter what happens."

"What! How dare a mere beggar speak such nonsense!"

Hearing that made him angry in a different way.

"Ah, father?"

"Ahem. It's nothing. Forget it. She said she wouldn't marry you? Can you tell me in detail?"

After hearing the circumstances, it was a bit ambiguous.

Was this a seductive ploy, or just a sister teasing her little brother?

It's something that can only be judged by knowing a person's gaze, gestures, and tone of voice, so it can't be known just from hearing about it.

Then there was only one way.

It's something you'd know if you talked to her directly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Peng Daesan was having the worst time of his life.

Even if he left the clan, women would just swarm around him annoyingly, so he just shut himself in and trained every day.

He even had an achievement and entered the Late Stage Peak Realm.

However, Peng Daesan did not stop training.

Because. Previously-

"Hey, little brother! I thought you looked at women like stones, but my, my. Tsk, tsk."

"What is it, elder sister?"

"I saw, you know? This, this. You sly dog."

Peng Chaolei poked Peng Daesan's side repeatedly.

For reference, Peng Chaolei has never had the concept of controlling her strength, so it's extremely painful.

Along with the pain in his side and the subtly, no, blatantly annoying slimy attitude, Peng Daesan's voice lowered a notch.

"What did you see?"

"That girl. Qing'er. She was pretty, wasn't she?"

Peng Chaolei said this with a sly smile.

Peng Daesan was dumbfounded.

Why that name suddenly?

"Do you mean Miss Ximen Qing?"

"Yes. That Ximen Qing. A friend, right? A friend, right? A frieeeend, right? That Jade Qilin's friend. Girl friend. Female friend. Lady friend."

To Peng Daesan, Peng Chaolei was more than a sister but less than a mother.

Peng Chaolei was the sister who raised Peng Daesan on her back.

This wasn't a metaphor but a plain fact.

Peng Daesan suppressed his irritation with that affection.

"Elder sister. I'm really getting annoyed, can't you stop?"

"Hmm, but you, you need to step up your game? She's about to reach Transcendent Realm soon. Since she underwent Overhaul Rebirth, should I say she's already gone there and come back once? Hey! Where are you going?"

"…I'm going to do wall-facing meditation. Don't misunderstand. I'm doing this because I feel like I'll really get annoyed if you keep smirking about that woman reaching Transcendent Realm."

"O.kay.I.got.it.Good.luck.my.little.brother."

And Peng Chaolei's expression he saw was so annoying that he felt like kicking away even the grace of being raised by her.

And then, oops.

Once the ‘unavoidable companion' comes to the Peng Clan of Hebei, it's literally impossible to avoid.

So he had to escape before that, but he forgot because he was too immersed in training.