\chapter{Are You Acquainted With This Beggar? (4)}

Qing sighed deeply.

"Round and round we go, back to my breasts again…"

Qing looked at Murong Jun quietly.

His pure eyes sparkled with expectation.

"Hmm."

Qing tilted her head crookedly.

\textit{Is he doing this on purpose?}

"But why the breasts of a stranger beggar, damn, that sounds so wrong. Well, don't you have an older sister or something?"

"Um, I do have an older sister…"

"Is she pretty? No wait, that's not it. Then-"

"My sister is very pretty! But don't you know my sister? She's very famous. Among the Five Flowers of Wulin, the Golden Sun Sword Flower is my sister."

"Then why don't you go ask your sister, why. Hmm, wait. Why am I saying this? Anyway, why are you leaving aside family and- no. Huh. That's more strange, huh?"

Qing rambled on and briefly fell into an error.

\textit{Is it worse if it's between siblings? Is it better than strangers?}

While Qing was confused, Murong Jun brought up unsolicited stories about his sister.

"My sister went to meet a friend in Hebei, and we're going to wait here until my sister and her friend come, then go to Kaifeng together."

"Then, to that sister's friend- No. This is a bit strange too. No matter how you go about it, it's weird. You little one, being so cheeky."

"The friend is a man, so…"

"Haiya, you really know how to slip out of things."

Qing admired.

Regardless, Murong Jun continued to bring up useless stories.

"But my sister has no breasts at all. She's even flatter than Uncle Yu who manages the garden…"

"Then, even if it's Uncle Yu, if you close your eyes, wouldn't it be similar? It's just flesh anyway. Hmm. But honestly, whether it's you or the uncle, basic human dignity would be hurt either way. But still. Hmm, I feel like I'm digging myself a deeper hole."

"But Uncle Yu's chest is all muscle. Even in the dead of winter, he says ‘A real man knows no cold!' and such."

Qing scratched her head vigorously.

\textit{Ah, Uncle Yu wasn't a plump person but someone belonging to the Zhuge department.}

\textit{But by the way, to be overshadowed by pectoral muscles…}

The unknown Golden Sun Sword Flower seemed a bit pitiful.

Of course, in Qing's experience, there's no benefit to having them big.

They always make your shoulders stiff, and when sleeping, no matter what position you take, the pressure is uncomfortable, and when it's hot, the sweat makes it miserable, so there are absolutely no advantages.

Although this discomfort disappeared after Overhaul Rebirth.

Even so, it's a big problem as a martial artist.

You can't see the lower part of your vision, making you vulnerable, and it limits the range of arm movements.

Last time, she got half-cut because she unnecessarily took a hit that could have been avoided, just causing pain.

It creates not one, but three fatal weaknesses for a martial artist.

Of course, the Peak-Transcending Ximen Qing is powerful despite this.

Still, she didn't envy the Golden Sun Sword Flower.

\textit{But why don't I envy her?}

\textit{Well, that's because my proud breasts-}

\textit{Hmm…? Why, why am I proud of them?}

\textit{What good is it for me to have breasts…}

It felt like she shouldn't think about it any further.

Qing hurriedly brought up something else.

"But you don't just listen through that secret passage, you even peek? How do you know your sister has no breasts?"

"No, I saw when we bathed together during the Mid-Autumn Festival."

Mid-Autumn Festival is a holiday roughly equivalent to Thanksgiving.

But to think that they would be bathing on Thanksgiving.

Qing burst out laughing.

"Mid-Autumn Festival, you say. It's not like you go to the bathhouse once every holiday to scrub off dead skin. But the Mid-Autumn Festival? What about the Spring Festival?"

Spring Festival is a holiday roughly equivalent to New Year's Day.

"That's not it, I asked why my sister, even though she's a woman, has no breasts and is flat like a man, but she got angry and since then she won't bathe with me anymore…"

"You really drove a nail into your sister's heart, huh.."

"So I can't tell my sister. She'll get really angry if I talk about breasts. I think it's too much, though. My sister doesn't even have breasts…"

The child puffed his cheeks as if dissatisfied.

\textit{It's not your sister who's too much, it's you.}

But Qing found it amusing, so she didn't say it out loud.

Hmm. At this point, Qing made a judgment.

He was just a curious, smart kid who hadn't learned to distinguish between what should and shouldn't be said.

Full of curiosity, he couldn't help but listen to others' conversations while running around in secret passages.

Being smart, he just remembers it all.

As for being loose-lipped, that's a characteristic of all little kids.

Once they start talking, they'll blurt out their entire life story until their voice goes hoarse.

In the end, Qing was soft on children one way or another.

\textit{Still, the child seems like a really good kid…}

\textit{From the way this precious young master of one of the Five Great Clans consistently used honorifics when speaking to servants, it was proof of his pure character.}

\textit{Just look at Tang Lan-Ah.}

\textit{Not just servants, but even when calling unknown old people passing by, it was either 'Hey' or 'You there'. Honestly, if she wasn't a female physician doing free service, a truly terrible woman would have been born into the world.}

"You shouldn't say such things carelessly. Didn't your sister seem upset when you said that?"

"Oh. You're right…"

"How would you feel if someone went around telling people you wet your bed?"

"Ah."

The child's eyes wavered.

At this, Qing was certain.

\textit{This kid, he did wet the bed.}

"I wouldn't like that…"

"Right. You understand what I mean?"

The child nodded.

\textit{As expected, he is a good kid at heart…}

\textit{Just the fact that he could understand made him top-tier in personality among little ones.}

As Qing's crooked posture became comfortable again, Murong Jun urged her.

"But when can I suck your breasts? I'll get scolded if I wander around for too long…"

"No, what? Did I leave my breasts with you and forgot about it or something? Are my breasts laundry? Suck my breasts? You're a little Sex Fiend in the making. You'll become a great pervert."

"But you took the gold sycee- Ah, oh no! The uncles must be looking for me! The breasts will have to wait for next time!"

Only then did Qing realize that she hadn't returned the gold sycee yet, and also that she hadn't told him how cruel and inhumane a crime it is to covet a woman's breasts who isn't your lover.

Murong Jun tapped his small foot with a Kong sound, then gently rose and cut through the air.

It was excellent and extraordinary Qinggong unbefitting a child.

Watching the rapidly retreating back, Qing shouted.

"Hey, take your gold sycee! Hey! Little Sex Fiend in the making!"

And thus, one bright yellow gold sycee remained in Qing's hand.

It was even brand new, untouched by human hands.

Of course, whether dirty or clean, the value is the same.

But it wasn't something a beggar should use.

Moreover, in fact, Qing wasn't in urgent need of money.

If she just went to a pawnshop and pawned Moonlight Sword (No. 9), it was obvious they would give her a pile of gold sycees because it was such a great sword.

Since a pawnshop is a place where you can get it back later by paying extra, she could just get it back with the chit book when she met her Sworn Sister in Kaifeng.

But if a beggar goes around buying food, it stands out much more than a clean female martial artist.

And the mindset is completely different between not being able to eat because you don't have money to buy food, and like now, where you could eat expensive dishes to your heart's content if you wanted to, but deliberately don't.

"I should return this, but…"

If she went to the dojo where the Murong Clan was staying and said 'I'm Ximen Qing. A great elder of Daoism, ahem', she could meet the little pervert in the making.

\textit{But why should I?}

\textit{Anyway, the kid seems to have a persistent side, so it's obvious he'll come back.}

\textit{I'll return it then.}

\textit{And while I'm at it, I should give him some sex education.}

\textit{If left like this, a Sex Fiend who will properly ruin one of the Five Great Clans, making it the Four Great Clans, will be born.}

Qing reflected.

\textit{Come to think of it, when my master was guiding me, didn't she apply that harmful radioactive substance to her fist while holding back tears?}

\textit{Thanks to that, her disciple was reborn as a proud righteous female expert like this… Ah, I miss my master.}

\textit{A child's education should rightfully be done by the family.}

\textit{But that doesn't mean I should just watch that state because it's not my child and none of my business.}

It's an adult's duty to guide a lost child.

So it was time for Qing to fulfill that duty as well.

\textit{This little brat. Just you wait.}

Qing began to set up her mental nuclear armament like a dictator.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tonight's dinner was at Xiliang Restaurant for a change.

Xiliang Restaurant always gave generous portions, so their treatment of beggars was really good.

If you just give ten coins and ask for a set meal, they'll give you a tray filled with the stir-fries they made in large quantities that day.

In fact, business isn't great because the taste is a bit inferior among restaurants.

Instead, they compete with quantity, so it's a middling restaurant that's not doing poorly either.

Their alcohol generosity was especially good.

Even if it's all sour spoiled alcohol, it can be used as a substitute for vinegar in cooking.

The generosity of pouring spoiled alcohol into a bowl because it's spoiled is a virtue hard to see in businesses.

But what's worrying is…

"The Flower Beggar has come again."

'Flower Beggar' is what they call Qing at Xiliang Restaurant.

In fact, Xiliang Restaurant isn't just being nice to Qing out of generosity.

It's because when they bring food, she stuffed herself so deliciously (it's not an insult, "stuffed" is the accurate expression) that quite a few customers come in, fascinated by that sight.

Thanks to this, they wanted her to stay longer, so the amount of food they gave Qing was gradually increasing.

Qing, not knowing the circumstances, just thought the hospitality was getting better because she was a regular customer.

Qing knew nothing but the way of beggars.

"It's starting to get hot these days."

"Yes, it's completely spring during the day now. Well, shall I bring you a set meal again this time?"

"Yes, please."

\textit{Damn, I shouldn't get too close with them.}

But it was not because Qing wanted to; it was just that while she was pretending to be a beggar to avoid making connections in preparation for assassins, she ended up becoming familiar with other people.

\textit{Should I stop coming here too now…}

\textit{Hmm, having these thoughts makes me feel a bit…}

\textit{This makes me seem like those kind of people.}

For reference, in Qing's homeland, there were extremely introverted solo diners who would quietly stop visiting when the staff started recognizing them because it made them uncomfortable.

To Qing, it seemed like an overreaction since you could just exchange a few greetings, it's not like you have to chat with the staff the whole time, but to each their own - everyone has their own struggles and the size of those struggles differs.

The server brought a tray with a mound of barley-rice-bran mixed steamed rice, various stir-fried vegetables, and a large bowl of alcohol-

\textit{My goodness, they gave two bowls!}

Qing smiled.

She was in the middle of heartily devouring her meal with some drinks when…

Crash, bang, clatter.

There was a commotion inside the restaurant, followed by hurried footsteps approaching.

Soon, customers rushed out urgently, some pale-faced and others with smiles on their lips.

The former were people who were surprised, and the latter were those already accustomed to the common inn disturbances in Jianghu, happily thinking someone was trying to dine and dash.

From inside the restaurant came the clang of blades clashing.

Qing frowned deeply.

What kind of people are fighting with blades in a cheap restaurant where you don't even need to spend a silver sycee to eat your fill, not a fancy inn, tea house, or specialty restaurant?

\textit{I'm so curious. Let's quickly go and watch.}

Qing crept stealthily into the restaurant.

The stealth technique Qing learned from the Demonic Cult, Black Shadow Stealth, was a whopping Red-grade technique.

It was a skill that even the server crouching behind the long table under the single seats could hardly detect.

"What's going on here?"

"Walla! You startled me! Ah, it's the Flower Beggar? Ahem, why are you here again? Don't embarrass yourself and stay outside."

The server, whose tone only becomes dignified when speaking to Qing, let his original accent slip out for a moment due to surprise.

"Watching fights is the most fun, isn't it?"

"Fights are one thing, but what would we understand watching Wulin Masters fight? It's only fun to watch thugs fighting on the street."

He meant that only low-level fights are fun to watch.

Qing nodded in agreement.

"To me, thugs or these guys are all the same. Hmm. So anyway, what's going on?"