\chapter{Are You Acquainted With This Beggar? (4)}

As she waited unobtrusively by the entrance next to the door, the waiter soon handed over a tray.

Six dumpling buns, one soup, and a large bowl brimming with alcohol.

Even if it was outside meal times, this could still be considered great generosity.

"Wow, thank you. You'll be blessed."

"Ahem. Eat quickly and go."

Qing sat down with her large bottom firmly on the ground in an unobtrusive corner and started eating.

First, she unwrapped the jerky from her travel bag and dropped it into the soup, then quickly took a sip of the alcohol poured full in the bowl.

The slightly spoiled hwaju, sour and stinging, blazed up as it seeped into her completely empty stomach.

"Hiya, that's good. The hospitality here is really nice. I shouldn't come often."

You should only go to hospitable shops occasionally.

After all, if a beggar goes often, the hospitality worsens.

Their generosity was honestly amazing, with even a large chunk of radish in the soup.

Dumpling buns taste the same everywhere in Zhongyuan - bland, tasteless, and dry.

If there's no mold, they taste the same whether from a fly-infested restaurant or the best restaurant in the city.

So, as she slowly chewed the dumplings, because one-wen dumplings have no taste and need to be chewed slowly to taste a bit sweet, Qing thought mechanically.

In fact, even now, if she knocked on the door of an orthodox sect in the city and sold her master's name, she could receive the utmost hospitality.

Even without that, if she used her monstrous strength to help with carpentry work, it wouldn't be a problem to eat three meals a day.

But if someone rushed at her shouting 'A walking bounty!' while doing that, innocent people would likely get hurt.

It was just a situation where she felt sorry to get close to anyone.

Qing, being the highest authority who should be enshrined with the status of a scholar even for vile tricks, knew well that she would have to step in if someone took an innocent person hostage again.

\textit{Oh, well. Let's just live as a beggar for a while. Whatever.}

At any rate, it's not even two months until the Wulin Conference.

Living as a beggar was only miserable when she had no skills and didn't know the ways of the world, but now she was rather worried it might be too boring.

After finishing her meal, Qing stood up briskly and began preparing for a full-fledged beggar life.

First, change into the clothes provided by the sword thief.

The torso area was a bit loose, but the sleeves and trouser legs are a bit short.

She washed her martial uniform vigorously at the laundry place and hung it on the communal clothesline, then went to the fabric shop to buy the cheapest cotton cloth and wrapped it around her feet, ankles, and up to her calves above the trouser legs.

This was the famous beggar foot wrap.

This concludes the preparations for beggar life.

It might seem too simple, but what grand preparations are needed to live as a beggar?

They're beggars because they live without such, after all.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ten days passed in the blink of an eye.

With the appearance of an unfamiliar female beggar, and moreover, carrying two swords, the city people were initially wary and looked at her with suspicious eyes.

But since she just sprawled out harmlessly without doing anything in particular, their wariness soon faded away.

If you asked whether a beggar with two swords was strange or not, you'd get an ambiguous answer like, 'Well, it's not exactly strange, I suppose'.

This is because traditionally, authentic beggars use dual canes.

The most traditional begging method is to block someone's front gate, stand there beating two canes held in both hands in rhythm while singing.

The lyrics vary by region, but generally say they won't leave until they're given food.

This method is impossible nowadays.

It was an era where clubs flew instead of food. Instead of not leaving from the front gate, you might just leave for the afterworld forever.

So now, this traditional begging method was a scene you could only see at celebration feasts commemorating good events.

Meanwhile, this essential item for beggars that served as a cane, self-defense weapon, and percussion instrument was called a "tagu-bong" (dog-beating stick).

You might think this is an ignorant name promoting animal abuse.

But the person who gave this name "tagu-bong" was none other than Confucius, the father of Chinese philosophy.

To summarize very briefly, it went like this:

Pan Dan asked Confucius:

What if I go begging and the homeowner has a big dog, making it difficult?

Confucius angrily replied, "They dare!"

Then, "Beat the dog!"

And the beggars famous for using this tagu-bong martial art were the Beggar's Union.

The headquarters of the Beggar's Union was in Kaifeng, and Changyuan City, close to Kaifeng, was completely dominated by Kaifeng beggars.

And finally, the beggars' fierce territoriality was about to extend its claws to Qing as well… but.

"Ah. The knots. You're from the Beggar's Union. Is Grandpa Lu Gu doing well? I'm pretending to be a beggar for a while due to circumstances, so please understand."

"Ah. You know the Discipline Elder? How do you know each other?"

"Due to circumstances, I can't say, but is he coming to the Wulin Conference this time? I'll greet him then, I guess."

"Ah. Yes. Then have a pleasant beggar life."

The Three-Knotted Beggar, branch leader of Changyuan, said this and withdrew.

It was the 'we are who we say we are' of Orthodox Wulin.

If it turns out to be a lie later, it's not too late to give a beating then.

But if they messed with someone who really knew them, things could go wrong.

So it's unconditionally beneficial to believe.

For now, all they could do was send word to headquarters that there was a female beggar claiming to know the Discipline Elder, gather the Beggar's Union members and tell them not to pay attention or talk to her unnecessarily.

Moreover, with the Wulin Conference approaching, important guests would be passing through, and there was no benefit in causing unnecessary disturbances.

"Kya. As expected, Zhongyuan connections are powerful."

Qing had been preparing for a battle with the beggars, but she didn't expect things to be resolved so cleanly just by dropping one familiar name.

It was almost unfair compared to her past struggles.

With no one bothering her, Qing half-dozed pretending to beg, sticking to the ground in the sunlight during the day.

Because of this, she was wide awake at night with nothing particular to do.

Moreover, lying down all day made her body stiff and sore all over.

Finally, unable to bear the boredom, Qing started training in the middle of the night.

How bored must she have been to swing swords in the middle of the night?

Days continued like this, sleeping during the day and training at night.

You could say she was living a more diligent martial artist's life than when she was enjoying luxury as a female expert of Wulin.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As the 25th day of March passed, it started to feel a bit hot in thick cotton clothes.

Still, it was chilly at night, making it just right for training.

Today too, with her money pouch spread out, she was pretending to be a corpse on a straw mat she had gotten from two Beggar's Union members.

Light footsteps approached, then stopped right in front of her with a presence.

Qing checked the visitor with her eyes half-open.

A kid who looked about ten years old was looking down at her like a strange animal.

Just by looking, you could tell he was wearing good clothes, and his face was flowing with nobility, so anyone could see he was a young master from a rich family.

He had a sword at his waist, so he seemed to be from a martial arts family.

Well. With the Wulin Conference not far off, he must be a child a family is taking to Kaifeng, she thought.

\textit{Come to think of it, Kaifeng was said to be close by from here.}

\textit{Well, that has nothing to do with me.}

Just as Qing was about to close her eyes again.

"Excuse me."

"What."

Qing answered unenthusiastically with her eyes closed.

"You know."

"I don't, so why don't you go away?"

"I have something to ask…"

The child's voice trailed off dejectedly.

Honestly, she felt a bit sorry for him.

Damn it. My weakness is being too soft-hearted.

Despite everything, Qing was weak to children.

Qing sat up, scratching her head vigorously.

"What is it?"

"Ah. You know. You're a female beggar, right?"

"Can't you tell by looking?"

"Then you must be a dirty prostitute? Right?"

"…?"

Qing's eyes narrowed.

\textit{What's this?}

\textit{I was going to exchange a few words because he was cute.}

\textit{But what's with this insult flying at my face?}

Of course, Qing didn't tolerate insults.

"Kid, have you ever been told you don't have a mother? From what I see, you look like you don't have a mother."

"Ah."

The child's eyes widened to about twice their size, becoming round with surprise.

"How did you know? They say my mother passed away giving birth to me."

"Ah. Is that so."

Qing answered indifferently.

Even so, she wasn't sorry for a brat who called her a prostitute bitch to her face.

"If you're done, will you go away now?"

"Um, well… This…"

The kid held out a large gold sycee with his tiny hand.

\textit{What's this? Suddenly a peace offering?}

\textit{Well, with this level of sincerity, I should show adult-like generosity.}

\textit{It was too much money to refuse, after all.}

As Qing accepted it, the child asked with a bright smile characteristic of children:

"Then, can I suck your breasts now?"

A vein popped up on Qing's forehead.

"Kid. I don't know what kind of home education you received to be so rotten already. Hey. Where did you learn these manners? Where did you learn only bad things, are you picking a fight with me? Don't you see I'm carrying swords?"

"Huh? That's not it…"

"What do you mean it's not?"

The child said with a tearful face:

"I heard that prostitutes let you do whatever you want if you give them a gold sycee…"

"No, who said that? There are things you can and can't say to a child. Go tell your mom right now- oh, you said you don't have a mom. Go tell your dad. Go ask him who taught you how to suck a prostitute's breasts."

"They didn't teach me, I just overheard the porter uncles talking. They said they were going to suck prostitutes' breasts. Oh, is it because it's a gold sycee? If I give you silver…"

"I don't know if you are stupid or innocent. No, seeing how you came determined to suck breasts, it's not innocent. Did those porters also say that all female beggars are dirty prostitutes?"

"That's what Warrior Bai ('White'. Baek in the original text) said. He said all female beggars are dirty prostitutes without exception, so we shouldn't go near them…"

"Who's this Warrior Bai- Alright. Let's summarize. So this guy called Warrior Bai said female beggars are prostitutes, and the porter uncles said you can suck prostitutes' breasts if you give them money, right?"

"To be precise, they said you can do whatever you want, biting and sucking and kneading like dough."

"And you want to suck breasts."

"Well."

The child blushed.

"I heard the kitchen aunties talking, they said their sons still fondle their mothers' breasts even after turning ten…"

"Then you should do it to your mom too- Oh. You said you don't have one. So?"

"So another auntie said that even very young male brats can't forget the taste of breasts and search for it all their lives, and I'm really curious what that taste is, but I don't have a mother, so…"

Qing frowned, dumbfounded.

"No, what? What kind of household can't distinguish between what should and shouldn't be said? It's a house with children, for goodness sake."

This is why households with children should be careful with their words.

What on earth is the child learning from?

But listening to it was kind of interesting.

Qing asked again in a much gentler tone.

"Is there anything else you overheard?"

"Umm… When touching breasts? They said not to touch the nipples, but gently scratch around them, and when the flood comes, then pa-ba-bak! and you go to paradise. What's the flood, and what's pa-ba-bak? Why go to paradise? Isn't that where good people go when they die?"

"Hmm. I can't teach you that. Alright, and then? Didn't you hear anything else?"

"Ah! And also…"

All sorts of lewd stories poured out of the child's mouth.

Qing, who liked naughty stories, kept saying "And then? And then?" until the child had nothing more to think of.

"I think that's all."

"Hmm. I see. I heard you well. By the way, did they really say such things in front of you?"

"Well… No… There's a secret passage, and while wandering around, um… I learned that eavesdropping is bad, but… They were talking so interestingly…"

Originally, she was going to tell him to go to his father and repeat everything he just said.

But now it seems the servants weren't particularly careless.

He said he eavesdropped from a secret passage, so…

Men might talk about naughty things during work, after all.

How could they have thought their young master would be eavesdropping from a secret passage?

It would be too harsh to make them lose their jobs over this.

But does this kid always go around eavesdropping on people in the house?

As Qing was thinking this, the child suddenly seemed to remember something and introduced himself, clapping his hands:

"Ah, right. I'm Murong Jun \footnote{慕容駿. Moyong Jun (모용준) in the original text}."

"Murong? The Murong Clan? That Murong Clan? Where was it again…"

"If you mean the Murong Clan of Liaoning, that's our family."

"Ah! Right. That's it. Liaoning Province."

Now even Qing knows at least the surnames of the Five Noble Clans.

She even knows where they are if told.

\textit{Wait, what? He isn't just any young master.}

\textit{He's a very rich young master.}

"I'm, um. Just a beggar."

Qing lied, not wanting to get close due to circumstances.

Some genius tracker or famous detective assassin might be listening, and it would be a big problem if a precious young master got involved.

At this, Murong Jun smiled brightly and said:

"Then, can I suck your breasts now?"