\chapter{Are You Acquainted With This Beggar? (2)}

When people sleep in a warm, well-heated room, burying themselves comfortably on an expensive bed, they fall into a deep sleep akin to fainting or losing consciousness.

Conversely, when closing one's eyes on cold, noisy, hard ground with stones digging into it, sleep is as shallow as a puddle after rain.

Such shallow sleep settles somewhere between sleeping and being awake.

You can't tell if you've actually slept, whether you've just closed your eyes for a moment or simply passed a long time with your eyes shut.

Qing, with her eyes closed, curled up even more.

It's cold. It's damp. Only where the sun shines is warm.

She thought she had a good dream.

A dream where she met a good master and good friends, living in luxury, wearing nice clothes, eating delicious food, and traveling around.

\textit{Hmm. Was it a dream, or not?}

Qing opened her eyes groggily to check.

A world on its side, people passing by clicking their tongues as if they'd seen something they shouldn't have.

Qing closed her eyes again.

\textit{Ah. It was all a dream.}

\textit{No wonder such good things couldn't happen in this damn medieval China.}

\textit{I'm so hungry I feel like I'm being torn apart. Please, let me have just one rat today, Lord Rat. I want to eat meat.}

\textit{Or I'll go to Pyeongchan Chaeru and- ah right, those bastards said they won't give out pork anymore.}

\textit{Ah. I don't want to move.}

In her first year, Qing originally didn't move.

Moving unnecessarily only made her stomach emptier and nothing nutritious happened.

At best, if she caught the eye of beggars, she'd get beaten up.

She would only slyly look around and eat something when her body was so weak that she felt she might die if she didn't eat anymore.

That's when it happened.

A presence was felt in front of Qing, who had her eyes closed.

Qing opened her eyes slightly.

Beyond the blurry texture of the face veil, she saw two feet standing suspiciously on the ground.

Rolling her eyes as much as possible, she saw the owner of the feet bending at the waist in her slanted view.

As the arm moved carefully and delicately, she rolled her eyes until they hurt and saw a familiar-shaped sword hilt in that hand.

It was the hilt of Moonlight Sword (No. 8).

\textit{Huh? Moonlight Sword?}

In that moment, Qing's mind, which had been in a strange boundary between dream and reality, snapped back to its place.

\textit{Wow, fucking hell. I thought I'd gone back to that time.}

\textit{And, of all things, I happen to come across a sword thief?}

'Sword thie' is an unfamiliar term to Wulin practitioners.

'Sword robber' might be more familiar and comfortable.

This is because a martial artist's weapon is like a concubine (for Chinese people, wives are mere family), so if someone else touches it carelessly, it literally leads to bloodshed.

Therefore, a martial artist's weapon is not something to be stolen, but something that can only be taken as a memento after killing them.

Qing quietly watched, pretending to be asleep.

As the sword was slowly pulled out of its scabbard, the blade, which could hardly be said to be well-maintained, gradually appeared.

And finally, when it was completely out…

"Where do you think you're going!"

Qing's kick drew a line parallel to the ground about an inch high.

The thief's ankles caught on it and he floated up into the air.

Thud!

The sword thief landed on his shoulder, then his chin hit the ground second, and as his arched back returned, his pelvis was thrown to the ground third.

"Haha, trying to steal a martial artist's sword, you must have truly lost your mind!"

Qing shouted as she jumped up and pinned the sword thief's wrist under her foot.

Her face was so bright it was almost as if she was greeting a long-awaited lover.

"Aagh! Hand! Hand! Hand!"

"According to the law, thieves are to have their hands cut off. Do you dare defy the sacred rule of law?"

Sacred rule of law? Both the concepts of sacredness and rule of law would be deeply offended and curse at this.

Throughout history, sacredness has never once been sacred, and the rule of law has been a high wall erected from birth to protect the interests of the privileged.

And the fact that she was spouting nonsense showed that Qing's mind was in a perfectly sound state.

"Really, these people are so mean. They couldn't just warn me about someone stealing my sword? Instead, they just watch?"

Qing glared at the street.

Because of the face veil, it just looked like she was scanning her surrounding, though.

Still, along with her words, the spectators who had been watching with interest subtly averted their gaze to look at the ground or sky.

Meanwhile, the sword thief kept screaming.

"Hand!! Hand!! Hand!!"

He should have been in enough pain to try to escape the situation by kicking Qing's ankle or something.

But he was in a daze from the pain that felt like his wrist was about to break.

All he could do was try to grab the shoe of the young woman and somehow create a gap.

\textit{Hmm? This is?}

Qing changed the pressure she was applying with her foot.

"Hand! Hand!!!! HanD! HaND!! HAND! HAND!!! HAND!!!!!"

\textit{This is kind of fun.}

\textit{It seems that his voice gets louder the more I apply force?}

Qing's mouth curved into a sadistic smile.

But that was only for a moment, as Qing checked the sword thief's Evil Karma and removed her foot with a regretful expression.

\textit{What a shame.}

\textit{If it had been just three points, three points higher, I would have been good to go.}

Only then did the sword thief shed a storm of tears, clutching his wrist and making a sound somewhere between sobbing and groaning.

Qing, who had picked up the Moonlight Sword, stood crookedly looking down at him.

"Hey. What are you crying for when you got caught stealing? You touched a martial artist's sword? Do you know what that means?"

"Hup."

"Everyone, you saw this bastard trying to steal a sword, right? You know that according to Jianghu law, it's not a crime to behead him, right!"

"That's right!" Someone shouted in response.

It seemed they wanted to see blood in broad daylight.

In fact, one of the greatest spectacles of this era was the beheading show where the head goes thunk, blood fountains spurt, and the body rolls and collapses.

It wasn't necessarily because Zhongyuan were uncivilized; in this era, beheading shows were extremely popular among all races worldwide.

It could be called a universal human sentiment.

Still, if we had to rank them, Zhongyuan people only enjoyed beheadings visually and politely.

They were much better than Westerners who would get red-eyed with excitement, pushing and shoving each other to dip bread in the flowing blood, causing chaos where people even died from being trampled.

"Now. If you understand, get in position with your neck out. I'll send you off painlessly in one strike."

"P-Please spare me!"

"You touched a martial artist's weapon, of all things, and you're asking to be spared? Would you show mercy to someone who touched your wife?"

"M-My wife has already run away with another man…"

"Umm. Well… Hang in there."

The scene became solemn for a moment.

Qing hadn't intended to kill him anyway, so she would have forgiven the man no matter what he said.

Even if it wasn't that his wife ran away, but instead it was some primitive ancient contrived melodrama about his old mother. Or something something about how his wife was like a daxiang and his children were the banes of his existence.

For reference, "daxiang" is "elephant" in Zhongyuan language.

"Alright. It seems you have a sob story, so I'll spare your life. Hand over everything you have and get lost."

At this, the sword thief untied his travel bag and money pouch and placed them meekly in front of Qing.

"Can I go now…"

"Are you kidding? I said hand over everything. I don't have a hobby of watching men's dangly bits, so I'll let you keep just one pair of underwear. Do it."

So the not-at-all-pitiful sword thief took off all his clothes, revealing silver pieces tied and hidden around his ankles with strings.

"What the hell? This motherfucker. Even though I spared your life, you still hid silver pieces?"

"Ah! Why are there silver pieces here! Who tied silver pieces to someone else's ankles! How strange indeed!"

The sword thief said something awkward that anyone could see through as he untied the silver pieces and placed them on top of the travel bag.

Qing said, dumbfounded:

"This crazy bastard is talking nonsense. Should I just butcher you?"

Qing didn't have a Black Flame Dragon on her left arm or a subordinate spirit to say 'Calm down' and stop her killing intent, so her right arm holding the sword raised with a terrifying murderous aura.

"Eek!"

The sword thief ran away in a flash, wearing only his underwear.

Along his escape route, the ground was stained black, leaving an irregular line and countless scattered droplets.

"Hmm. He's pissing himself, huh."

The watching commoners also fled in terror.

Even a peerless Master under heaven would step aside in fear if a dark man came running while pissing himself.

Thanks to this, the sword thief quickly disappeared.

Qing looked at the spoils left behind.

"Hehe, sweet, sweet."

The money pouch had about a handful of coins.

And one silver piece, which felt like about a quarter of half a silver sycee when lifted.

Although it was just small change not even amounting to one silver sycee in total, she was overjoyed to have obtained a travel bag.

The travel bag looked empty and sagged limply, seeming to have nothing inside at first glance.

But the bag itself was important.

She already knew from her first year how big a difference having a bag or not makes.

Still, looking inside to see if there was anything, there was one dirty towel and something wrapped in an oiled broad leaf.

"Ooooh, jerky."

For jerky to be delicious, it needs to be a high-quality product made as a delicacy.

This was dried miscellaneous meat so tough that teeth couldn't penetrate it, with questionable hygiene, the common and ordinary kind of rations that anyone would eat.

But it was at least something.

Even if it's smelly and tough to eat as is, if you soak it in soup for a long time, you can at least feel like you're chewing meat.

Grumble.

Thinking about meat made her insides clamor, telling her to stop doing stupid things and put in some food.

"Hmm. Should I eat? I should have some dumpling buns and knock back a drink for the first time in a while."

Anyway, it was better to fill up on cheap dumplings and push down some strong alcohol rather than eating poorly cooked food.

The timing was just right.

Looking at the sun, it seemed to be about the end of the Horse Hour and beginning of the Sheep Hour, around 3 PM in Qing's units of time.

\textit{What the heck? I slept quite a long time.}

\textit{It doesn't feel like I slept at all though.}

Anyway, at a time that's neither lunch nor dinner, inns usually sell food even to beggars.

Of course, they can't eat inside, but have to sit in an unobtrusive spot in front of the shop.

Human hearts are truly fickle.

When she thought all her Jianghu adventures were a dream earlier, she felt heavily depressed and didn't want to live, but now that she was about to act like a beggar again after a long time, it felt somehow familiar and nostalgic.

It was natural since she could escape this beggar status at any time.

Come to think of it, she could just pretend to be a beggar and pass time, then go to Kaifeng on the right date.

Who would imagine the bounty in question would be a beggar on the roadside, after all?

Qing scratched her head vigorously as she slunk around looking for a suitable restaurant.

If it's too high-class, she'd be turned away at the door, and if business is too bad, they'd give out things that have gone bad from not selling, so those had to be filtered out.

So she had to find a decent place where the staff's expressions were bright and the atmosphere was good.

There also needed to be a good place to eat in front of the shop.

At that, Qing found a suitable place to eat.

Xiliang Eating House.

An eating house was just one grade lower than a restaurant.

Qing pretended to be cautiously looking around at the entrance of the eating house.

As a server approached with a tense expression at the appearance of a sword-carrying beggar, Qing deliberately spoke in a very subdued voice to order.

"Um, five dumplings please. And do you have any really cheap but really strong alcohol…?"

Beggars are originally just beggars, but beggars who know martial arts are Esteemed Beggar.

And here, the Esteemed Beggar in question was carrying not one but two swords, while politely placing an order.

Moreover, even if she must be an ugly woman since her face is covered, her voice was strikingly beautiful.

The server's self-esteem soared to the sky.

As the server's shoulders rose, his attitude noticeably softened.

"Where in this world would there be cheap but strong alcohol?"

Strong alcohol is expensive.

Because strong alcohol is made by compressing weak alcohol through evaporation or other methods anyway.

"Even spoiled alcohol is fine…"

"Hmm. Please hand over one more coin. I shall bring you something suitable."

The server's tone of speech was extremely old-fashioned.

When else would a server get to use such an adult way of speaking?

This was all wisdom gained through life experience.

As a female expert of Wulin, Qing would be considered an idiot. However, as a beggar, she had already surpassed any regular beggar and possessed wisdom worthy of being called a sage.

She was truly a beggar by nature.