\chapter{Are You Acquainted With This Beggar? (7)}

"Um, you should have just woken me up."

"But you were sleeping…"

"I wasn't sleeping. I was just lying down."

"Then, now can I-"

"Stop! Stop the sexual harassment! Stop the sexual violence!"

Qing said firmly, showing her palm.

This was a miraculous solution from Qing's homeland that stopped the other person's bad behavior and simultaneously made the delinquent shed tears of repentance, reform, suddenly realize the joy of friendship, help each other study hard, and solve all problems at once.

It was devised by the great officials of the Korean people, and among such miraculous and great products was also a mysterious object called a laughing bell that made people burst into laughter with happiness when rung.

\textit{Damn, I haven't finished organizing the gender equality education yet.}

\textit{I thought he'd come a few days later, not suddenly in the middle of the night.}

\textit{When was the last time I heard this?}

\textit{It was five years ago, before I left for Jianghu.}

\textit{What I remember is…}

\textit{Thinking back, I know what attitudes I shouldn't take.}

\textit{Like not treating the audience as sex offenders.}

"Hmm. First, I'll return this to you, and the breast talk ends here. Understand?"

"Ah. Yes…"

\textit{How should I put this… It's not very childlike to accept it without throwing a tantrum here, isn't it?}

\textit{He seems to listen well.}

"And come sit here. Your Dage will tell you some awesome stories."

"You were a Dage (big bro)?"

"Dage can also mean someone older."

"Ah…"

Murong Jun sat down on the ground with a thud.

"First, let's do a diagnosis. Well, hasn't anyone taught you what you should and shouldn't say to others? Is the basic education of the Five Noble Clans lacking? What do they teach in the clan?"

Even Tang Lan-Ah knows what she shouldn't say.

She knows, but she just does whatever she wants and if it becomes a problem, she gets through it with an excellent apology.

\textit{Come to think of it, this kid at least asked. Tang Lan-Ah just groped in secret.}

\textit{It appears there was a real sex offender elsewhere.}

"Martial arts!"

"Hmm. And?"

Then Murong Jun made an expression as if asking if there was anything else to learn besides swordsmanship.

"How old are you, kid?"

"Nine years old!"

"And you haven't learned anything besides swordsmanship?"

"Yes! They say I'm the hope of the clan! They say I just need to work hard on martial arts. And martial arts are fun!"

Seeing him fly away with Qinggong during the day, it was a skill unbelievable for a nine-year-old.

He must be a martial arts genius, or a martial arts prodigy or something, but still, they should teach him some basic common sense.

This was Qing's thought, who was likely to be ranked first as the person with the least common sense under the heavens, about the adults of Jianghu.

But well, it wasn't strange.

In Qing's homeland too, weren't there many parents who didn't care about their child's usual behavior as long as their grades were good?

Thinking they'll get better as they grow older.

If grades could solve everything, how could they get better just by growing older?

They were like parents smiling at their child's report card, not knowing they were preparing to be abandoned in old age.

"Alright. First, listen. In the world, there's something called chastity…"

Qing conducted her version of Chinese-style gender equality education.

Qing wasn't so ignorant as to suddenly teach complete gender equality in Zhongyuan.

However, she fully agreed with Ximen Surin's radical ideas - which were radical only in Zhongyuan but common sense by modern standards.

The primitive, ancient, uncivilized Chinese level was exactly like this: if a woman showed her bare feet, it was like losing her chastity, so it was grounds for divorce and okay to beat her and drive her out.

(Beyond China, the West wasn't different given the time period)

Murong Jun's expression, which was curious at first about what she was saying, gradually turned into a tearful face.

"…So if it wasn't me with my broad mind, our little one would have done something so bad in the world that he'd have nothing to say even if he was killed with a sword. Understand?"

"Uh. Then, did I do something wrong…?"

"Yes. If you did something wrong, what should you do?"

"This…"

The child fumbled and held out the gold sycee that had been returned earlier with his tiny hand.

\textit{Look at that hand! It's like a quarter of mine!}

\textit{Four of them would match mine perfectly! My goodness!}

But cute is cute, and wrong is wrong.

Qing, as a sensible adult, had a duty to teach that there are opponents in the world where cuteness doesn't work.

Thwack!

It was a crisp sound like bamboo swords clashing.

"Ow!"

Naturally, Murong Jun grabbed his head and rolled on the ground.

Shaolin Monks don't need to learn useless supreme techniques like the Seventy-Two Shaolin Fist Arts to enlighten evildoers, saying they'll guide them.

To reform evildoers, Ximen Surin's Radioactive Fist Bombing Technique is enough, so this unprecedented technique should be widely spread in Wulin.

"Ah, it hurts…"

Murong Jun had large teardrops hanging from his eyes.

"If you did something wrong, you should apologize first. Offering gold comes after that. Understand?"

"Yes… But Beggar Sister, am I not bleeding?"

It was exactly the reaction someone else had made.

\textit{I know that pain.}

Qing held back her laughter and admonished him.

"Stop rubbing it since you're not bleeding. And remember that pain. My heart hurt like that too. How dare you call a stranger a dirty prostitute? Well, I was dirty because I'm a beggar. But still, why a prostitute? Do you know what prostitute means when you use it?"

"Uh, someone who does anything if you give them money…"

"Bzzt. Wrong. Ignorance is not an excuse. Don't try to understand on your own. You should have checked with an adult first."

"Yes… Then, Beggar Sister is an adult, right?"

He was asking to be told.

"Of course. There's no adult as great as me. Hmm. In the world, there are good words and bad words…"

Qing conducted her version of education suitable for a nine-year-old child.

It was childish content like 'Don't say bad words, it hurts the listener's feelings'.

However, it was also precious education that no one had given Murong Jun, but should have.

It wasn't that the Murong Clan people were ill-mannered.

A genius who was certain to become the Greatest Under Heaven in the future had appeared in the family, so they were excited about teaching martial arts which he absorbed so well, and took turns acting as teachers all day long.

They wanted to be able to say 'I taught the Greatest Under Heaven' later and clear their throats proudly.

Thanks to this, thinking 'Someone else will teach common sense', by everyone including you and me, this disaster occurred.

"…So you shouldn't use such words."

"But adults already use them freely."

Qing was momentarily at a loss for words.

\textit{Ah, so that's why they talk about mirrors and such.}

\textit{Of course, the clan members probably talked freely because they didn't know the child was eavesdropping.}

\textit{Is that secret passage the problem?}

"Hmm. Still, adults already know they're bad words when they use them."

"Then isn't that doing bad things?"

"Yes. That's right. Instead, if problems arise because of it, they take full responsibility themselves. Hmm. Yes."

The child was too young to be told about personal responsibility.

Qing had never thought so carefully since coming to Jianghu, so if Ximen Surin had seen this, she would have praised her for already becoming an excellent teacher.

"They're bad adults. So, does our little one want to be a bad adult too? Will you become a bad adult with them?"

"Hmm… I don't want to."

"Right. Good boy."

Qing patted Murong Jun's head.

It would have been better if her hand wasn't dirty.

\textit{Hmm, the crown of his head is a bit swollen.}

\textit{Did I hit him a bit too hard?}

"But, you know…"

"Yes. What?"

"About breasts…"

Hmm. But the kid has a persistent side.

However, his next words were pitiful.

"Then is there no way for me at all? I can't do it because I don't have a mother. And I don't have a wife because I'm not married. If it's bad to do it to other people…"

"Sadly, that's right."

"That's unfair…"

It was a pitiful thing to say, but those words were right.

\textit{But how should I explain this?}

\textit{I can't spout nonsense like 'You rich young master born with the best silver spoon in Zhongyuan! How dare you complain about your blessings?'}

"Hmm. Don't you have any mother at all? Damn it, why am I talking like this? It keeps coming out wrong. No other mothers? In a rich family, aren't there usually several mothers? Ah, right, a wet nurse! Don't you have a wet nurse?"

"Well, she became my aunt…"

\textit{Did the wet nurse and uncle fall for each other?}

Qing thought simply, but the reality was a bit more complicated.

A wet nurse was roughly in the position of an honorary wife, so she wasn't a servant but just not registered in the family tree, and was practically family.

Neither Qing nor Murong Jun knew, but there existed a great victory of pure love that overcame everyone's opposition when a man took his brother's honorary wife as his main wife.

However, only Murong Jun, who had no mother and now had his wet nurse taken away, became a bit pitiful.

"I'm sorry. There's no other way. You'll have to get married quickly, I guess?"

"Yes. Um. But…"

Murong Jun looked at Qing.

Qing made a troubled expression behind her face veil.

\textit{Oh dear.}

\textit{I really don't know why kids like me so much.}

\textit{This is why they have cute aspects.}

"I'll tell you in advance, I have no intention of getting married. No matter how much you look at me like that, I won't make a marriage agreement."

"Huh. I don't want to marry Beggar Sister either."

Qing's eye twitched.

"What's this? Didn't you just look at me with eyes that said ‘What about you?' No changing your words because you're suddenly embarrassed, okay?"

"Well, I was going to ask if marrying for breasts would be doing something bad to the other person…"

"Hmm. When you teach one, they learn ten, or so they say. You've had a very good thought, little one. The little pervert in the making has now become Jianghu's number one eligible bachelor."

Qing wiped her hand on Murong Jun's hair again.

\textit{It's still swollen.}

\textit{I hope no one comes chasing after me later asking who hit him.}

"Hehe…"

The child made a clear laughing sound, pleased.

\textit{Hmm. He's a child, a child.}

\textit{But I should question what needs to be questioned.}

"But you said you don't want to marry me? How dare you?"

"But Beggar Sister wears a face veil. People who wear face veils do so because they have faces that might upset others if seen…"

"Who said such a thing? Is this another eavesdropped story?"

"Father said so… There was someone wearing a face veil before, and when I asked why that person covered their face, he answered. He said they're covering their face for others, so we shouldn't point fingers or try to peek carelessly."

"Hmm. I see. You know well."

This is why you should listen to everything.

Given how people in Zhongyuan perceive those wearing face veils, and since the conclusion was excellent, the father spoke correctly.

Qing, who just covered her face because it was bothersome, is a special case.

It wasn't like there were absolutely zero people in Zhongyuan who use it for that purpose, but there was no need to emphasize the unusual minority.

Suddenly, Qing's mouth curved into a mischievous smile.

"So, you don't want to marry ugly me? Come to think of it, I might be willing to marry our little one now. Want to think about it one more time?"

"No. I'm going to marry a pretty woman."

"Isn't personality more important than looks?"

"Uh… Then, I want to marry a woman who's both pretty and kind-hearted. Not Beggar Sister."

The child answered after thinking for a moment.

It was truly a clever answer.

"Ah, when a rich young master says this, I have nothing to say. Alright, so you're going to marry a woman who's both pretty and kind-hearted? Think carefully. This is your last chance. If you reject me this time, I'll be so hurt that I'll never marry you."

"Hmm… I'm sorry."

The child bowed his waist while sitting.

Seeing that, it seems he's been well-educated.

"Really? Then there's nothing I can do. I don't want to marry you either. Even if you cry and cling to me later, it won't work."

"I don't think that will happen…"

"It's over now, completely over. Eternal friends. Understand? Don't expect more than friendship from me. Got it?"

"Huh? We're friends?"

Murong Jun's expression changed to one of happiness.

At this, Qing's expression also became pleased.

"Yes. Want to be secret friends with Sister?"

"No. I want to be just friends, not secret friends."

"You keep having these firm moments…"

"Then, since we're friends, you can call me A-Jun. Then Beggar Sister…"

"I'll give you special permission to call me Flower Beggar Sister."

"Huh? Flower Beggar…?"

Murong Jun looked at Qing's face veil with an awkward expression.

\textit{By the way, about this brat.}

\textit{Why does he take a crooked path every time he's about to be cute?}