\chapter{Are You Acquainted With This Beggar? (11)}

The Peng Clan of Hebei arrived in Changyuan City around lunchtime and unpacked at the Changyuan Daoist Temple.

Although the Changyuan Daoist Temple was only ranked fifth in Changyuan City, it was in accordance with Clan Leader Peng Xian's principle that Daoists should naturally stay at Daoist temples.

Thanks to this, only the angry Changyuan Daoist Temple leader was busy excitedly welcoming the important guests.

This allowed the beloved disciple Zhang to show his face at the Dragon-Phoenix Assembly gathering of the Wulin Conference.

Of course, after the introduction, building personal relationships was entirely up to Zhang disciple, but…

After roughly unpacking, or more precisely, after finishing giving instructions with just her fingers, Peng Chaolei teased her younger brother, giggling like the hooligans in the marketplace.

"Loosen up your expression. You'll get wrinkles between your eyebrows. What if my brother's beauty is ruined? It's not just your problem, it's a loss for the entire Wulin world."

"Next time, I'll tell Father to find three marriage candidates and put them in the same carriage with you, sister. He'll surely welcome it, saying a man must compete, so your words are indeed right."

"But shouldn't there be two to be fair? We should include a woman too-"

"You mean a woman who emanates killing intent towards you whenever she makes eye contact with a man?"

"Hmm. I'm sorry. It must have been very difficult."

Peng Chaolei apologized readily, shuddering.

After that, the usual things guests should do followed.

Exchanging pleasantries, having lunch together.

After eating, drinking tea and exchanging more pleasantries.

Meanwhile, Peng Clan Leader Peng Xian's title was 'Daoist Gentleman', because he was very generous in imparting teachings to other orthodox Daoist sects.

When Peng Xian said he wanted to see the Changyuan Daoist Temple's skills, they were so honored they were on the verge of shedding tears of gratitude as if they had seen the Emperor.

In fact, Peng Xian wanted to be called the Dao King, like the Sword King Nan'gong Daero, the clan leader of the Nan'gong Clan whom he considered a rival.

But he gave up because he couldn't dare use 'king' in his title so close to Beijing.

Normally, Peng Daesan would have also gone to the training ground with his father to train together.

But due to the great fatigue from traveling, especially the overwhelming mental fatigue, he just went to his room and quietly fell into meditation while circulating his qi.

After some time had passed, a servant came looking for Peng Daesan, saying there was a guest looking for him outside, asking what to do.

"I'm tired now, so please decline."

"Well…"

The servant hesitated and said.

"It's someone I can't dare to stop, so they're already here."

Just then, as if on cue, a man with dark skin appeared.

"Haha, right. Don't blame him too much, he couldn't help it. So, why are you cooped up in this room on such a nice spring day?"

"Brother Cao."

It was Cao Haocai, the heir of the Black Dragon Cao Clan.

"Come on, don't be so stuffy, let's go out."

"Just this morning you were grinding your teeth so much. Do you still have teeth left?"

"Haha! I'm sorry, sorry. But don't dwell too much on past events. Is it the first time I've acted like that?"

"Brother Cao, please be more mindful. You completely lose your senses whenever you see a woman."

"What can I do when there's no sense left to be mindful of? Isn't it the sad fate of a man for all his senses to be focused solely on flowers?"

Peng Daesan let out a deep sigh.

This was exactly who Cao Haocai was.

All the men in the Dragon-Phoenix Assembly evaluated Cao Haocai as a true man they'd want to emulate when there were no women in the group.

Or they called him 'that woman-crazy bastard.'

Somehow hearing this gossip, Cao Haocai laughed heartily and brushed it off, saying, "Yes, I'm Cao Haocai, a crazy bastard who'd give his life for women," showing his broad-mindedness.

But he was the very person who had been grinding his teeth and emanating killing intent towards Peng Daesan for ten days straight.

"Come on, let's go."

"Going to a brothel right after unpacking, what on earth will people think?"

"What will they think? They'll just say the bee is going to the flowers. But this time, it's not that."

"You mean you're not saying we should go to a brothel?"

Peng Daesan asked back with a surprised expression.

It was because this man was not the type to avoid brothels, even more than a drunkard quitting alcohol.

"Right. Actually, I heard something interesting."

"It's never actually been interesting, not even once."

"No, listen. You'll find this interesting too, Brother Peng. There's a unique female beggar in this city…"

"It's already not interesting. Please go back."

Peng Daesan cut him off flatly.

"No, no, just listen?"

"I don't want to hear it. Why don't you keep it to yourself and share it when Brother Changbin comes?"

"Brother Changbin turns into a stone statue when women are involved. Even though he talks like he's the greatest flower-admiring young master under heaven."

"It would be nice if we could combine the two of you and split it in half."

"Haha! Then wouldn't that be completely my loss!"

Three furrows appeared between Peng Daesan's eyebrows.

"Where was I in the story?"

"Brother Cao. Please come to your senses. I can understand high-class courtesans, but a female beggar? Surely you're talking about those who sell their bodies."

"Right, you're right, brother. I was talking about the female beggar. Just listen."

Peng Daesan pressed his forehead firmly.

\textit{Why don't people listen when someone speaks?}

\textit{Perhaps, did I actually not speak?}

"There's this female beggar who covers her face."

"Good heavens. She even covers her face?"

"But they say her body's figure is amazing. They say she's a living hourglass figure. Isn't it interesting already? Her face is ugly but her body is that of a beauty."

"It's not interesting at all."

Peng Daesan cut him off again.

Of course, it didn't get through at all.

"Right, it's interesting? But they say this female beggar's night skills are so excellent. They say it's like going to paradise."

"You believe that? Isn't it not much different from what Brother Changbin always says?"

"No, no, don't be surprised. They say the female beggar tells them to pay as much as they enjoyed, and the least amount is one silver sycee, with many men paying ten or twenty sycees, and someone even paid four gold sycees."

At this, Peng Daesan's eyebrows twitched.

"…Indeed, that is a bit surprising. Men usually change their minds after finishing their business. You're saying they willingly paid that much?"

Even in brothels, there are quite a few men who try to avoid paying and get beaten up, but they willingly paid that much money to a mere female beggar?

"That's why they say it's like going to paradise. It seems she started her business when it got warm after rolling around in the cold, and in just half a month, half the men in the city have tasted paradise, they say."

Peng Daesan's expression soured.

"How can that be…"

"That's why it's even more surprising. They say it takes less than half a quarter of an hour to finish the deed, so she receives a hundred customers a day. Half a quarter of an hour. How can they be so satisfied and offer gold and silver in such a short moment?"

Peng Daesan's expression soured even more.

If someone had seen it, they would have been surprised that a sour expression could become even sourer.

"Brother Cao, you have a strong stomach. Isn't it disgusting? Isn't she a whore rolling in the gutter? No, the gutter would probably be cleaner than her."

"Don't worry. They say not a single person has gotten sick in the past two months."

"That's not the issue."

"If it's not disease, what's there to hesitate about? It's not like she's a woman to take as a wife. Anyway, let's go."

"I won't tell you to enjoy it either, so just come with me. Since it's only half ke, wouldn't it be enough to just stand there and guard a bit? I ask you just this much. Okay?"

Paengdaesan took a deep breath.

It was because he knew that Cao Haocai was not the type of person to listen to rejection anyway.

"In that case, we're just going to see that beggar. And don't ask to go to a brothel afterward."

"Haha, that depends on the female beggar. If I'm satisfied after visiting paradise as rumored, would I still want to go to a brothel?"

"You're not saying you absolutely won't do it."

"I can't lie, you know. Haha!"

In the end, Peng Daesan, who was forcibly dragged out, had an expression as if he had bitten into a bug.

Nevertheless, the wall of women who swarmed around, squealing 'Oh my, how handsome!' 'How can even his frowning expression be so handsome!' were just busy blushing and gazing dreamily at the Jade Qilin's jade face.

"Brother Cao. Even like this, do you really have to embrace that female beggar? All the women in the city, no, those annoying stalkers beyond the city will tell all of Zhongyuan that Brother Cao slept with a beggar."

"Hmm. A man shouldn't back down. And anyway, aren't I already the guy crazy about women? If I can experience paradise…"

"You're really crazy."

Peng Daesan shook his head.

It was truly madness incarnate.

If this wasn't called madness, what else could be called madness?

And so, two men and hundreds of women swarmed across the main street.

And finally, they arrived at the female beggar's dwelling.

If you can call a spread straw mat a dwelling.

As the two reached the sunny corner, hundreds of women surrounded them in a semicircle.

If they spread a net of heaven and earth like this, no one would be able to escape.

However, there were only two straw mats at the spot, and the place was empty.

"It seems she's not here."

"Hmm. Should we wait? Or is she receiving a customer? Ah, oh."

From a narrow alley slightly to the side of the beggar's spot, a man came out rubbing his head with bloodshot eyes.

The poor man was startled by the wall of women spread out as soon as he came out and didn't know what to do.

Cao Haocai grabbed the man.

"Hey, friend. It seems that female beggar has set up her brothel over there?"

"Ah, yes, yes! That's right!"

"Really? No way. Have you been crying?"

Cao Haocai couldn't hide his admiration seeing the tear marks left on the man's face.

"How moved must you have been for a grown man to shed tears! So, how much did you pay?"

"Well, one gold sycee, seven silver sycees, and thirty-two copper coins…"

"My goodness! Judging by the odd units, it seems you gave all the money you had! Am I right?"

"Yes, yes, that's right…"

"Good. Did it really feel like you went to paradise?"

The man felt like he wanted to die.

His head was beaten, he gave all the money he had, and now he had become a man who slept with a beggar in front of all the women in the city.

And then he couldn't let only himself suffer.

"Yes. I briefly saw my late grandfather, didn't I? I definitely went to paradise. Well then, I'll be going now."

And then, unable to break through the wall of women, he slipped out sticking close to the wall.

"See that? It's certain."

"Enough, why don't you go in and do your business?"

"Come on, man. After finishing business, a woman has things to take care of too. Is it manly to just barge in?"

"You're already doing things a man shouldn't do."

"Oh, there she comes out. Indeed, she's voluptuous, her figure is completely different. What do you think?"

"…"

"Hey, Brother Peng? Jade Qilin?"

"…"

Getting no answer, Cao Haocai turned around and smiled mischievously.

"This friend is completely dumbstruck. Why, are you moved now that you've seen her with your own eyes?"

At that moment, Peng Daesan strode forward.

Then he firmly grabbed the female beggar's wrist and forcefully led her beyond the narrow alley.

"Wh-where are you going? Brother Peng! You have to follow the order!"

Cao Haocai, who was suddenly cut in line, smiled awkwardly.

And then.

"No way!"

"Jade Qilin! No! Come back!"

"Kyaaah! How can this be reality…"

"Hey, snap out of it! Open your eyes!"

All sorts of screams, wails as heartbreaking as if tearing one's liver, and lamentations burst out at once.

Some fainted and lost consciousness to the point of passing out, while some who were enraged immediately tried to rush into the alley, but.

"Oh my. Young ladies. You mustn't dare interfere with a man's cloud and rain pleasure. My heart burns like fire to dare point a sword at you flower-like beauties, but I can't let you ruin my most beloved brother's first experience."

With Cao Haocai blocking the narrow alley and unleashing his sword qi, what could they do?

However, at the words 'cloud and rain pleasure' and 'first experience', more women fainted again, and only terrible screams echoed as if tearing the sky in broad daylight.
