\chapter{Are You Acquainted With This Beggar? (12)}

Meanwhile, Qing, who had returned after sending one guy away, was surprised.

\textit{What's this wall of women?}

\textit{As if some Jade Qilin had appeared.}

\textit{…No, he really did appear?}

Qing pondered for a moment.

Should she pretend to know him or not?

The conclusion came quickly.

There's nothing to gain by pretending to know him now.

After that distribution, she'd just click her tongue with a blank face while pretending to be a beggar.

She'd have to see him in human form at the Wulin Conference.

As Qing was considering her escape angle, suddenly…

Peng Daesan, approaching urgently with large strides, grabbed her wrist and pulled.

"Ouch, what are you doing?"

"Shut up and follow me."

In fact, she could shake him off easily if she wanted to.

Not just shake him off, she could even grab him and swing him around like a weapon.

But rather than breaking through that wall of women guarding the Jade Qilin and escaping, it was more advantageous to take the alley first, so she obediently let herself be dragged along.

However, that chatterbox was not obedient.

"Oh my, why are you doing this? No matter how urgent, you shouldn't do this. First, you should set the mood gently. Hmm. It won't break even if you squeeze that hard."

Suddenly feeling pressure squeezing her wrist, Qing said.

The beautiful wrist of the White Hand Demonic Arts, which contends for first place among the Ten Great Demonic Arts under Heaven, is an indestructible vajra that wouldn't break even if hit with a hammer, let alone grip strength. Due to insufficient realm, it's not invulnerable, but extremely difficult to break.

"You, what on earth have you been doing? What's all this?"

Qing flinched.

As a Peng Daesan expert, his friend's voice burst out in the highest danger level ultra-low frequency voice from the start, according to his mood-based vocal range classification.

Qing tried to play it off.

"Ah. Did I get caught? You recognized me well. Wow, is this what they mean by having a good friend? Long time no see, San."

Peng Daesan's eyes trembled violently.

It was the most terrible form among all possible scenarios of meeting a female friend.

Reuniting with Ximen Qing was the worst.

"Just what, what have you done, the man who just left…"

Peng Daesan's voice trembled.

If Peng Chaolei had heard, she would have known it was a sign of an impending explosion of anger, but Peng Chaolei was the highest authority who had raised Peng Daesan on her back, so how could Qing know?

"Ah. That guy? I don't know why there are so many guys like that these days. A perfectly fine guy tried to harass me in broad daylight, so I beat him up, extorted some money, and chased him away."

"What?"

Peng Daesan's expression suddenly twisted.

Remembering the subtle expression of the harasser with evident tear marks, it meant that his words about seeing his grandfather in paradise and returning actually meant he was beaten and briefly fell into the Yellow Springs before coming back to life.

The deep relief was short-lived, followed by anger erupting like an active volcano.

"Ha. You call that an explanation? What? Beat him up and extort money? For that bit of money, your face- no, do you even have any intention of living with your head held high in Zhongyuan?"

"San, my friend, first calm down a bit…"

"Do I look like I can calm down? Ha, do you know what all the men in the city are saying about you?"

"Um… There's a foul-tempered female beggar who beats you up if you touch her?"

"Ha. They say there's a beggar prostitute who sleeps with a hundred men a day as the city's specialty. Even though I just arrived around lunchtime today, I've already heard about it."

"What?"

Qing's expression also soured.

"These damn bastards, which bastard spread such rumors? Who, who said such things?"

"All the men in Changyuan."

"Damn it."

Qing's insides boiled.

\textit{What's this and that?}

\textit{Alright, I was wrong, I was wrong.}

\textit{I should have just burst their heads with the delicious taste of the Black Slaying Demonic Palm instead of a head flick.}

"This won't do. Which bastards are they? I'm going to cut their limbs into star shapes."

The light in Qing's eyes gradually disappeared.

Seeing Qing unable to hide her anger and instead raging, Peng Daesan's energy drained.

"Haah. Alright, I understand you didn't know either. What on earth were you doing pretending to be a beggar without picking up even one such story?"

"No, I didn't hear anything."

Qing spoke with an aggrieved voice.

Of course, how could Qing, a woman and the person in question, hear stories circulating among men?

"…First, you should explain why you're in that beggar's appearance."

"Ah. This? Well, how this happened is…"

Qing explained what happened in Zhumadian.

Old man sob sob. Unorthodox faction boom. Silkworm pupae nom nom.

The strange choice of the human trafficker who chose to become a eunuch over receiving a gold sycee.

And the ten thousand gwan bounty.

"…So I didn't want to cause trouble for anyone, and to avoid being seen, I was disguising myself as a beggar."

"Really, haah. Should I say this is just like you?"

Hearing this, Qing had done nothing wrong.

Moreover, the Black Spot originally deals with all sorts of poisons, drugs, stolen goods, slaves, and even human flesh, a collection of the worst scum.

"Well, it's fine. Anyway, only three people know my identity, no, including our San, only three, right? I've already got promises from two people. You'll keep it a secret, right, San?"

Anyway, the flower beggar of Changyuan would soon disappear even without that.

The only people who know her identity are A-Jun and his father, and his father agreed to pretend he didn't see her, and she talked to A-Jun well, and he's a kid who listens exceptionally well, so there's no problem.

The Beggar's Union treated her like they couldn't see each other after she mentioned Grandpa Lu Gu's name, so they don't know anyway.

So if she just leaves, it's over.

The flower beggar will disappear from the world.

"Ha, with that body of yours, you think you can just disappear?"

"What's wrong with my body?"

"Are you asking because you don't know? Is there another woman among Jianghu women with that height and that vulgar- no, big. Hmm… broad figure?"

Peng Daesan said, somehow avoiding eye contact.

Qing burst out laughing.

"Why are you choosing your words? Why can't you say ‘vulgar tits worth three demerits'?"

"…You remembered that. And I didn't say such vulgar words as tits, damn it."

"Ah, was that Xue Ganom?"

"Just what kind of Ganom (bastard)- ahem, I'll withdraw the demerits, so please just forget it."

"No way. I'll never forget it for the rest of my life. And, people judge surprisingly by appearance? If I'm wearing beggar clothes, I'm a tall beggar, and if I'm wearing Divine Maiden Sect uniform, I'm seen as a female martial artist of Jianghu. And well, what if I say I'm not?"

Peng Daesan was momentarily dumbfounded.

Come to think of it, occasionally, very occasionally, she did say such wise things.

That's when it happened.

"Wow, but how did you recognize me at a glance? Even though I've undergone Overhaul Rebirth and my limb lengths have changed?"

"Hmm. Still, you should be careful. Rumors, if they want to be malicious, can attach anything. If such a terrible scandal spreads in the world, what on earth do you plan to do?"

Peng Daesan changed the subject.

"San! Are you worried!? Wow, Ximen Qing is touched. A sea of tears of emotion. Don't worry. At times like that, I just need to reveal my face, right? Here, look. Ta-da!"

"Revealing your face won't change anything-"

Peng Daesan's words cut off abruptly.

It was the fate of someone who faced Qing's harmful face up close without mental preparation.

Just her bright smile like an innocent child, her eyes full of brilliant affection, her smile made of deep joy was so dazzling it hurt to look at.

And the red lips drawing a mischievous arc.

For some reason, in the world that suddenly turned gray, he couldn't take his eyes off that sole red color.

But that was only for a moment.

Qing didn't give him a chance to let his guard down.

"Look. I've become pretty, right? This is the power of Overhaul Rebirth. Ah. Overhaul Rebirth is really good, I can't explain it in words. You can't understand unless you experience it. Someone still doesn't know, right? How could a Mid-Stage Peak Realm know about Overhaul Rebirth? Ah, how pitiful."

\textit{That damn mouth.}

Peng Daesan's eyebrows twitched.

"Mid-Stage? I'm Late Stage Peak Realm now."

"Right, right, are you coming to your senses now? See, when you look at my face, you can't see anything else, right?"

"Ahem."

Peng Daesan, who fully understood its power, cleared his throat out of pride rather than answering.

Seeing this, Qing became triumphant.

"I did a proper job pretending to be a beggar because I had a plan. If I was ambiguously beggar-like, wouldn't everyone be suspicious?"

For a moment, Qing's Righteous Karma was deducted by one point.

In fact, she had no plan.

However, Qing, who didn't keep her status window open, didn't know.

Sometimes, ignorance is bliss.

"Then, what do you plan to do now?"

"The flower beggar will exit, of course. I was planning to just laze around until the Wulin Conference. But that won't do now. After I bolt like this, I'll take a bath in the middle of the night. Ah. You hate dirty things, right? Please understand. It would be strange if a beggar was clean, right?"

"It's fine."

Peng Daesan, who was usually very particular about cleanliness, unexpectedly gave a plain affirmation, contrary to expectations that he would be horrified.

\textit{What's this? Is it a friend privilege?}

\textit{Has this Peng Daesan finally realized the preciousness of friendship?}

"Ah. Right. If I disappear like this, won't it be troublesome for you, San? You'll become the guy who slept with a beggar who receives a hundred customers a day."

"Don't ever bring up that talk, even as a joke. It's something that should be hidden forever."

"Your voice is getting low again. Hmm, how about this? Actually, the flower beggar was a Great Demonic Adept hiding her identity, and San, the great expert of the orthodox faction who recognized this, chased her away after a fierce bloody battle."

Even Qing thought it was a very convincing story for something made up on the spot.

It could explain the disappearance of the flower beggar and simultaneously raise Peng Daesan's reputation, truly killing two birds with one stone.

"Then, I'll see you at the Wulin Conference."

"You're going to leave like this again?"

"Of course?"

"Becoming the guy who slept with a beggar doesn't seem so bad. No, rather it's good. Those annoying women following me will fall away, so isn't it a good opportunity? Moreover."

"Moreover?"

"Hmm. Never mind."

Peng Daesan swallowed his words.

If it were to be exposed later, the two of them matching their stories might seem even more suspicious, so he couldn't do that just in case.

But a man doesn't show off his good deeds.

"What? Why did you stop mid-sentence? There are two things that make people angry, and one is stopping mid-sentence."

Qing looked at Peng Daesan as if to show off.

Peng Daesan quietly waited for the rest of the words.

Only after a long staring contest did Peng Daesan realize he had been had.

"Forget it. Let's just go together and get an inn room. You can slip out after cleaning up completely. Why would a woman take a secret bath in the middle of the night, what if someone peeps?"

"Oh. San. I'm about to be touched again."

"Enough. After you slip out, come to the Changyuan Daoist Temple later. We have the same destination, so is there any reason to go separately?"

"I'm sorry, but that's not possible."

"What? Why?"

Peng Daesan's eyebrows twitched.

Qing answered with a serious expression.

"As a swordsman, I cannot endure the humiliation of staying at a half-sword sect. Ahem."

"Kuk."

Suddenly, Peng Daesan burst out laughing.

Though he was clearly trying to hold it in, his face turned red as he struggled to hold back the wind trying to escape.

"Why don't you just laugh if it's funny? Do you feel like you lose if you laugh?"

"I'm not… laughing…"

"Uh… hnng…"

"Kheuk."

Peng Daesan suddenly made a sobbing sound.

Even so, he stubbornly refused to let out the sound of air escaping from his lungs, truly showing his determination.

"Alright. So it's the Changyuan Half-Sword Sect, is it? Ah. Is Miss Peng there too?"

"That damn half-sword talk… If you mean my sister, unfortunately yes."

His laughter not completely subsided, Peng Daesan's voice went up about a semitone.

At this, Qing quickly changed her words.

"Then, it's back to the Changyuan Daoist Temple. As a friend who has shared the Dao with Miss Peng, insulting the Dao is like insulting me. If you say great sword, isn't it just two sword blades put together? From now on, I'll call swords twin daos. With two Moonlight Twin Daos, the day when the Moonlight Twin Daos roar is not far off."

At this, Peng Daesan's gaze towards Qing settled down completely.

It was a look that said, 'My goodness, how can there be such a woman in this world?'
