\chapter{Are You Acquainted With This Beggar? (8)}

"Why, I'm a Flower Beggar because I'm a flower-like beggar. Got a problem with that?"

"But, but you're fat…"

"Hey. Peonies are flowers and lotuses are flowers too, right? Are they not flowers because they're big?"

"But, those two are pretty…"

"You really speak your mind, don't you? Fine, you're so great. Alright. Now go. Flower Beggar, no, Beggar Sister is going to sleep."

"Ah. Um, well, then, um, pumpkin flower, no pumpkin flowers are pretty when you look at them, so how about just pumpkin? Or bitter melon or cucumber- Ow!"

Murong Jun rolled on the ground again, not realizing his expensive silk clothes were getting covered in dirt.

According to Qing's personal theory, kids are of the earth element anyway; they originally live by eating dirt, so it's okay for them to roll around a bit.

It was much weaker than before, not strong enough to dare attach the almighty name ‘nuclear', so it was just a regular head flick (Third-Rate).

But getting hit in the same spot again hurts much more viciously.

After rolling around for a while, this time Murong Jun seemed to feel wronged, and threw a gaze full of betrayal with eyes hanging large teardrops.

"W-Why?"

"I told you bad words aren't allowed."

"But Beggar Sister also said my father was right. People who cover their faces-"

"Enough. You, would you feel good if I called you a bed-wetter? Are you really telling me you've never wet the bed? Not even once until now?"

"Ah."

"What ‘ah'. Enough. Beggar Sister is sleeping."

Qing then lay down completely.

At this, Murong Jun stood still, just rubbing his crown slightly.

"Um, Beggar Sister. Isn't it uncomfortable to sleep here? Our house, no not our house, how about sleeping at Sohua Sect?"

No one could deny that the child was kind at heart.

Qing answered while lying down.

"You have to think about the people at Sohua Sect too. They won't like it if you bring a beggar, right?"

"Ah."

"Alright. It's late at night, don't wander around alon- Hm? Wait, what? What time is it now?"

Qing lay on her back and looked at the sky.

Judging by the position of the clear moon shining faintly, it was about the end of the Ox Hour to the beginning of the Tiger Hour, which translates to about 3 AM in modern terms, when people's sensitivity is at its fullest and they cannot help but send the famed '3 AM vibes' messages.

"No, what's a precious young master doing wandering around in the middle of the night? It's dangerous."

"Ah. I'm not alone. I came with Warrior Lu\footnote{綠, lit. 'green'. Nog (녹) in the original text} who guards me. Warrior Lu?"

"Keurk."

Suddenly hearing a phlegmy sound, she looked and saw a black-clad person looking this way from under the shadow of that wall.

Though his realm was unknown as he seemed to be hiding his aura, other information showed his Evil Karma was in the early 200s.

\textit{What? I didn't notice him at all.}

\textit{But wait? What the heck? Isn't he a bad guy?}

Qing became sharply alert.

At that, Guard Lu waved his hand as if to reassure her, and Qing was unsure but suddenly remembered Gramps.

\textit{Right, there could be people like Gramps too.}

\textit{The child is opinionated and persistent, but he listens well and is cute too.}

\textit{Murong Jun seemed like he would have made a fortune as the nation's little brother, a top visual child actor if he had come out in modern times.}

\textit{Wait, then does that mean he heard all the gender equality education I gave too?}

\textit{Why did he just leave it alone?}

\textit{Did he think it was content Ajun needed to hear?}

\textit{Well, I guess a sensible adult wouldn't ever stop such a beneficial lecture.}

\textit{But he wouldn't tattle about how I gave such loving strikes, right? The strikes that I had to endure the heartbreak of even daring to lay a hand on such an adorable kid?}

"Warrior Lu hurt his throat before, they say."

"Hmm. Your family will be worried. It's late, so go home quickly. You might not need sleep, but Warrior Lu must be sleepy."

"Warrior Lu is always awake at night. During the day, Warrior Bai guards me."

"You always have an escape route…"

Qing muttered, lying spread-eagled.

She was already fully awake and clear-headed.

Forcing herself to sleep here would just result in a short nap and a headache when she woke up.

There's nothing to do at night anyway, so I should just do some martial arts training.

"I'm going to train now. So if you're done with your business, go home and sleep. Sleeping at night makes you grow tall and such."

"Hasn't Beggar Sister slept too much?"

"What, kid? When I was young, sleeping only one and a half shichen a day was a child's virtue. They said if you sleep more than that, you can't become a great person."

That three-hours-sleep-five-hours-fail shit.

Which fucker said such things again?

For reference, 'three-hours-sleep-five-hours-fail' was a bad practice in the Korean people's harsh college entrance exam culture, meaning you pass if you sleep three hours and fail if you sleep five.

"Ah! My father said that too. He said two shichen of sleep is enough, so if you can't sleep, there's no need to force it, and if you're bored, you should at least train."

"So that's why you're wandering around now…"

It was hard to tell whether this father was strict or not.

But since the child didn't show any hesitation when mentioning his father, he must be a father who gives plenty of unconditional love.

"Then, train with me. I'm stronger than the clan's warriors!"

"This body doesn't cross swords with mere First-Rates. How about coming back after you've improved a bit more?"

"But it's good to improve together…"

Qing let out a laugh mixed with a snort.

"Alright, let's train. Training is what's left…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Murong Jun's father's words that two shichen of sleep is enough are roughly true.

First, Masters who have achieved Overhaul Rebirth can manage with two shichen a day.

And those who possess supreme techniques excellent at relieving mental fatigue were like that.

Qing fit both categories, but she just liked sleeping, so she slept a lot for a master.

Anyway, Qing's daily routine remained the same.

She lazed around during the day, ate a hearty dinner, immediately lay down hugging her full belly to enjoy a post-meal nap, and when she came to her senses, she swung her sword in the middle of the night.

With high probability, Murong Jun would appear at night and spar with her while keeping her company.

And with low probability, Murong Jun would also appear during the day and annoy her by disturbing her sleep.

"What is it, I need to sleep."

"You said one and a half shichen is enough…"

"I'm making up for not sleeping then. By the way, is that person someone you know?"

Qing pointed to a man on one side who was glaring at her as if she were his mortal enemy.

"Ah. That's Warrior Bai."

"But why is he glaring at me like that? Did I do something wrong?"

"It's not that. I told Warrior Bai he should apologize for calling Beggar Sister a dirty prostitute, and now he's like that. I'm sorry our warrior is a bad adult. I'll apologize instead."

"Oh my. How sweet. Yes, grow up just like this. The future of the orthodox Wulin is bright."

Qing patted Murong Jun's head.

At this, Warrior Bai put his hand on the hilt of the sword at his waist.

\textit{What's he going to do? Draw it?}

When Qing threw him a mocking sneer as if to show off, his expression changed as if he had bitten into a bug.

Warrior Lu with high Evil Karma was occasionally spotted and would bow politely when their eyes met, but this bastard leaning towards Righteous Karma was a completely ill-mannered scoundrel.

\textit{Saying things you shouldn't say to a child, this guy.}

So sometimes when the kid appeared during the day, she deliberately kept him company to tease Warrior Bai.

Time flew by like that again.

Originally, if there's nothing special and it's not particularly hard while the daily routine is regular, time passes quickly.

However, as you get older, you become accustomed to the ways of the world and special events gradually decrease, which is why time passes quickly for adults.

As spring starts to bloom, clothes become hot.

It's hot during the day and cool at night, so Qing, who was strong against the cold due to harsh training, tore open the seams and took out all the cotton.

She could treat it roughly since it was clothes she was going to throw away anyway.

"Beggar Sister? Did you lose weight? Suddenly?"

"It was because the clothes were thick. Hmm. But where are you looking? Is the little pervert in the making reviving?"

"Ah. I'm sorry. It was just surprising… Isn't it heavy?"

"It is heavy. But don't look so openly, others will gossip. Glance. Glance. Pretend not to look and glance."

Thanks to Tang Lan-Ah, Qing had become able to properly distinguish lewd gazes.

It wasn't Tang Lan-Ah's damp and desire-filled gaze, but truly just a child's curiosity sparkling.

Either way, curiosity doesn't last long.

And in reality, after a few days, Murong Jun quickly lost interest and stopped glancing.

However, other bastards were a bit of a problem.

"Even with your face covered, your figure is nice. Well, if it's an unsightly face, covering it is enough. Where's your nail warehouse?"

"Ah. Would you come this way?"

Nail warehouse refers to a brothel.

It means a place where you quickly nail in and then pull out, like hammering nails, showing how Zhongyuan people are quite good at wordplay.

Warrior Bai's words that all female beggars are dirty prostitutes were words that shouldn't be said to a child, but if you ask whether it's true or false, it did fall under the category of truth.

Lying on the street and glancing, you can't see the face anyway because it's covered.

But the lines the body draws, wow! My goodness! How can this be! How can it be like that! So a man's lustful heart and other things can't help but rise.

Qing, who had moved to an inconspicuous place in a back alley, nuclear bombed the crown of the man who was already untying his waistband.

Whack!

At the moment of impact, there was almost an illusion of his head being crushed into a concave shape.

It was the ultimate secret technique of Ximen Surin-style Complete Destruction Head Flick (The Staff of God) containing the meaning of punishment rather than admonishment.

"Where are you going in broad daylight, you perfectly fine bastard."

"Agh! I'm dying!"

"I hit you so you wouldn't die, so come to your senses. This is what happens when you get frisky carelessly. Got it?"

"You crazy beggar bitch, do you want to die- Hup. Your martial arts are quite strong. You should have said something in advance…"

The stone that was in Qing's hand turned into finely ground powder and scattered lightly.

The man who was about to shout angrily became docile.

"Now. You've learned a great life lesson that if you try to play with your dick anywhere, you might really become a dick, right? Leave the tuition fee."

"Yes, teacher. I'll leave it here."

"Good boy."

After taking out the cotton like that, Qing, who had knocked down three walking sticks just on that day, thought:

\textit{This should be enough for rumors to spread about a violent female beggar, right? They won't bother me anymore, right?}

Qing's thinking was short-sighted.

There was no way such rumors would spread.

How could a man say he got beaten by a beggar, and a female beggar at that, and even paid a hefty tuition fee before running away?

Rather, the opposite rumor spread.

‘What? You said you made a fortune today? Why don't you have any money? You said you'd treat us, are you changing your words?'

‘No, well, I gave some charity to that female beggar over there.'

‘Female beggar? You're talking nonsense. Isn't twenty wen enough? You say you were robbed of one silver sycee? Did you get beaten and robbed?'

‘No, that's not it, uh, yeah, she was so good, I was moved and gave her a bit.'

‘Hm? That good? Should I go too?'

‘Uh, that's, um? Yeah. You should definitely go too. It's something you really have to experience once in your life. I really almost went to paradise- no, I briefly visited paradise, I tell you.'

This was because the men whose money had suddenly disappeared avoided interrogation with roughly similar flows.

Along with the childish psychology that they couldn't be the only ones to suffer.

And so, ten days later, in mid-April when flowers were in full bloom and spring was brilliant, the money Qing had earned just from tuition fees filled her travel bag with silver sycees and coins.

"What's wrong with this neighborhood? Are they in heat? Don't rumors spread? Or do they want to get beaten? Should I quit pretending to be a beggar since even the Black Store is quiet?"

Qing grumbled after creating a large hill on another guy's head.

By the way, maybe because it's spring.

Everyone's coming out to bask in the sun.

It's really crowded with people.

Qing lazily lay down and watched people.

Suddenly, feeling a sense of incongruity, Qing tilted her head.

\textit{Huh. Were there always this many women in this city?}