\chapter{Are You Acquainted With This Beggar? (1)}

It was obvious to point out, but martial arts consume a massive amount of stamina.

The foundation of martial arts is stamina.

That's why almost all sects shared a training method for completely snot-nosed kids who could be roughly classified as Fourth-Grade disciples (though there's no actual title of "Fourth-Grade disciple"), potential third-generation disciples.

Horse stance and climbing mountains for no reason.

And fetching water for the sect to use.

Even throughout their growth period, it was the same process.

It might look like bullying or child abuse.

But this was a very important training that laid the foundation for martial arts by simultaneously training stamina and lower body strength.

Of course, there was also the advantage that it was very convenient to have the little ones fetch water.

At any rate, the stamina consumption of martial arts is extraordinary enough to require such a harsh childhood.

Give commoners a sword and tell them to swing it a hundred times.

They'll end up sitting down, panting.

And among martial arts, there was one that was the worst of the worst, draining stamina excessively.

And that was Qinggong.

Long ago, didn't a Westerner run about a hundred li to deliver news of victory and then drop dead, either from his heart bursting or lack of blood supply?

If you make commoners sprint at full speed right now, you'll see them expelling all their body's moisture through their entire body before even one ke passes.

That's one ke for Zhongyuan commoners; if you made modern people from Qing's homeland sprint at full speed, they wouldn't last even a minute before collapsing.

So, Qinggong was a difficult technique that required operating Inner Qi on top of that to add propulsion.

It's not just a concept of assisting running with Inner Qi.

It was a simultaneous task and double hardship of having to operate Inner Qi while running.

Moreover, the places where Qinggong is used aren't wide-open, well-packed sports fields without a single pebble.

It's rough terrain with steep ups and downs, where the ground to step on is covered with pebbles, fallen leaves, hidden puddles, slippery rocks, and so on, making even normal running difficult.

So maintaining Qinggong for a long time is very difficult.

It requires not only iron-like stamina but also perfect body control and balance, concentration to operate Inner Qi, and quick reflexes to deal with terrain where no two parts are the same in the world.

Ximen Surin didn't evaluate for nothing that there wouldn't be many people who could catch her disciple if she ran away.

It was thanks to superhuman stamina, balance, and Inner Qi control that she could circle Mount Wu and come back still fresh, without sweating a single drop or catching her breath even once.

The exceptions Ximen Surin mentioned were cases of quickly catching up to Qing over short distances.

Over long distances, as far as Ximen Surin knew, there was no one who could catch up.

She thought this would be true even for the Divine Thief, a master famous for having the fastest Qinggong under heaven.

And Ximen Surin was right.

The Divine Thief stopped, panting like a dog.

"Huff, wh-what, huff, phew, girl, huff, phew, doesn't, doesn't get, doesn't get tired. Huff."

No one had threatened him to talk to himself, but Divine Thief was chattering away even while out of breath.

If someone pointed it out, he might answer that it's because he's been a lonely old man for a long time.

In fact, just because someone's a lonely old man doesn't mean they talk to themselves a lot, so he was just born that way.

The Divine Thief's plan was simple.

One. Watch and observe from a distance.

Two. Appear at a dangerous moment and save her.

Three. Sternly and seriously offer to take her as a disciple.

Four. Receive the Bow of Discipleship from the Nine Bows of Etiquette.

Then, success!

But he was blocked from step one; watching from a distance, my ass.

What kind of girl runs non-stop for over two shichen without resting once, making the distance grow as his stamina depleted?

Even though the Thousand Li Flight was known as a Qinggong specialized for long distances, there should be a limit.

To the Divine Thief, the highest authority on Qinggong, she was just a girl born as a natural runner.

Feeling like his old heart wouldn't last if he chased any further, he finally had to stop.

"Phew, th-this, phew. At this, huff, time, phew, if she passes here, Wulin, Wulin Conference, phew, it must be the road to the Wulin Conference?"

The Divine Thief changed his mind.

Was it really time to play tag in the middle of the night with a young girl?

People should use their heads; in the end, he'd see her in Kaifeng anyway, so he just wasted energy in the night for nothing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Without even knowing that the uninvited guest following her had fallen away, Qing kept running.

She really didn't know anything at all.

Qing was quite serious when it came to eating and running away.

Rumors in Zhongyuan spread surprisingly slowly, only spreading from person to person face-to-face.

If she runs away faster than rumors and hides to settle down, who would know and find her, be it assassins or bounty hunters?

For now, she would sleep during the day and just get further away.

Running and running and running like that, as the sky began to brighten dimly, she had run for a full four shichen.

In modern terms, that's eight hours.

From about three shichen, even Qing started to get tired, so after four shichen passed, even Qing thought, "Wow, I can't go any further," and immediately collapsed spread-eagled on the ground.

Her body eagerly sucked in air, gulping down inhales and throwing out exhales.

Thanks to this, the inhales and exhales collided in the middle of her airway, giving a feeling of explosion, making her realize bodily that this is what it means when they say breath reaches up to your chin.

In the end, Qing lay spread-eagled on the ground.

People who have run to their limit would know (surprisingly, many don't), but the aftereffects include a wringing pain where not a single part of your entire body doesn't hurt.

The ground is cold but the body is hot, so that chill is rather welcome.

After lying like that for a while, hmm.

It's cold!

It was early spring dawn, as cold as midwinter, and she had sweated so much that her clothes were completely wet.

If she took them off and wrung them out, they'd probably pour like a waterfall.

She was in a state of wearing wet clothes and being thrown into a bitter cold.

The best condition for a person to freeze to death is when they're exhausted from sweat, their clothes are wet, and the weather is cold.

When she was wearing thin clothes in the Divine Maiden Sect, the wind could pass through but at least it wasn't damp.

Thinking she'd freeze to death if she slept here, Qing painfully raised her body, and her damp back was covered in black dirt.

But how would Qing know what her back looked like?

In that state, she took heavy steps and soon a high city gate blocked her view.

Seeing 'Changyuan'\footnote{Other translation translate it as Zhangwan, but Zhangwan is south of Kaifeng, while Changyuan, Xinxiang, is exactly between Kaifeng and Puyang} written on a large hanging plaque, she thought the city's name must be Changyuan.

As someone who doesn't know Chinese geography, Qing couldn't know where it was, but if others knew, it would be surprising news.

Who would believe that she had run about 600 li\footnote{about 300 km} from Suya Lake to Changyuan City all night?\footnote{Which means Qing sprinted with average speed of 42 km/h. For reference, marathon runners run 42 km with average pace of 10 km/h. The record of 100 m sprint still held by Usain Bolt, clocking at 9.58 s or equals 36km/h}

Changyuan is a city located between Kaifeng and Puyang.

Puyang is a passage connecting to Hebei in the north, so if you trace Qing's trajectory as she ran in a trance-like state, she had actually passed Kaifeng.

Just in time, as it was morning, the city gate opened.

Seeing the city, her empty stomach immediately churned.

She had literally run all night, after all.

Her stomach was hungry and her body felt sticky and uncomfortable.

"Ah. I'm dying…"

Qing groaned and headed towards the city gate.

With her face covered by a face veil, two swords slanted across her back at her waist, and a dark flute stuck in her belt at her side, she looked extremely suspicious. Like, what kind of woman is this?

But there was the non-interference between Wulin and the government.

Meaning, because individual officials were scared to deal with superhumans carrying swords and flying around, they didn't dare to catch her and were about to let her pass through the city gate.

Suddenly, the veiled woman with swords turned directly towards the gate guard, and the poor soldier gulped.

Then the veiled woman asked:

"Excuse me, where's a good restaurant around here? What do they do well?"

The soldier was greatly relieved.

"The Dacheng Vegetable Shop on Chengguan Avenue is good. They say the cook learned in Shandong, and they do Shandong cuisine really well, but whether it's real Shandong cuisine or not, well? Some people say it's not…"

"Chengguan Avenue. Dacheng Vegetable Shop. Thank you. Good luck with your duty."

Qing bowed her veiled face to the kind soldier and passed through the city gate.

As it was morning, merchants who had come out carrying their breakfast wares were selling soup noodles or half-soup dishes.

Qing's eyes darted around.

But with the strong determination to eat something delicious when she was so hungry for once, Qing tightly closed her eyes and looked away.

It's a loss to just fill up on something like that for one meal.

When you're hungry, delicious food tastes twice as good.

Soup noodles and bantan aren't anything special anyway.

\textit{Hmm. But what if I just taste a little?}

\textit{If you're too hungry, you can't eat well, right?}

How could the starving Qing resist food?

Unable to hold back, Qing finally reached for her money pouch.

Reached for her money pouch…

After groping the air a few times, Qing's complexion turned pale blue.

It was the first time since leaving for Jianghu that her complexion had been so pale.

\textit{The money pouch is… gone?}

Of course, it was all Qing's karma.

She, who could lift 500 jin as a world-class strongwoman, had entrusted all her luggage to her weak Sworn Sister, so she only knew how to carry swords and didn't know how to hang anything on her own body.

It was truly dog-like manners.

To be fair, Qing could also feel a bit wronged.

The culprits who created these manners were both the old bastard and young brat, Crutch No. 1 and No. 2.

Wasn't it because they begged and pleaded to carry things that she got into the habit of entrusting them?

The problem was that Qing didn't have a single coin, not even one wen in her possession.

"Ah."

Remembering the three coins she received from the martial arts manual merchant, Qing hurriedly felt all over her body.

But Zhongyuan clothing doesn't have pockets.

Of course, martial uniforms do have places sewn inside to put this and that, but she had quickly handed the coins to Jian Buxi when she received them, so only bits of cotton fluff stuck under her nails.

One coin could buy one empty dumpling bun.

With three coins, you could even get a soup without any solid ingredients as a bonus…

Qing had returned to her original state after a very long time.

Originally, Qing was a miserly poor person from the start.

Qing started walking for now.

Standing still made her wet clothes cool down and feel cold.

So she had to move first.

She was busy scanning the ground, rolling her eyes this way and that, wondering if there might be a coin dropped somewhere.

\textit{What should I do? I'm hungry. No money…}

Suddenly, tears welled up.

Qing shouldn't be hungry.

She might not know other things, but she shouldn't be hungry.

Moreover, just look at her state now.

Her clothes were damp and sticky, and she had no change of clothes, so there was no other option.

The weather was cold, her body was tired, and due to the aftereffects of long-distance Qinggong, her soles were on fire and the slight cramps in her thighs and calves were not normal.

\textit{Damn, this won't do.}

\textit{Let's get some sleep first.}

If she gets any hungrier here, it seems like she won't be able to sleep because of hunger.

Also, it was just cold; it was not like she would freeze to death, and rather than holding her hungry stomach and looking for dropped coins, it was better to sleep when she could.

Qing wandered around the city, looking for a place to sleep outdoors.

After all, sleeping outside was something she'd been doing since she set foot in Jianghu, so it was familiar.

Qing then found a good spot in the sun under a wall in a corner of the marketplace.

It was an open area with many passersby so it was safe, yet while visible, it wasn't a place where people would walk, so there was no worry of being kicked.

Moreover, if the sun was shining now, it would continue to shine until noon.

Despite not having slept rough for a long time, to find such a prime spot right away; this is why they say people should learn that experience gained through physical hardship doesn't disappear.

Qing lay down sideways under the wall and curled up like a shrimp.