\chapter{Are You Acquainted With This Beggar? (10)}

And so, currently.

"Ah, look at that, Young Master. The spring flowers have bloomed so beautifully."

"The azaleas blooming among the phlox are truly a rare sight, the finishing touch. Just like Miss Murong-"

"Young Master! Look! It's a deer, a deer!"

-…You damn Jade Qilin…

It was the Golden Sun Sword Flower Murong Zhuji\footnote{慕容珠姬. Moyong Juhui (모용주희) in the original text}, reporting on every single thing she saw.

And the grinding teeth sound was that of Cao Haocai\footnote{曹郝采. Jo Hakche (조학체) in the original text}, Brother Chao, the heir of the Black Dragon Chao Clan.

He was trying to flatter and make advances to the Sword Flower, but he was being treated almost like a non-existent person.

Every time he was ignored, he ground his teeth while looking at Peng Daesan, hostile towards another man just to gain a woman's favor.

Brother Cao was a really generous and good brother when among men (he'd be an even better brother if he didn't keep urging to go to brothels), but he had the strange habit of suddenly treating all men like enemies when a woman joined the group.

Anyway, women would just leave for a more handsome man when they meet one.

But friendship isn't like that, so if he had asked for help instead, I would have tried my best to help somehow.

Besides that, Brother Cao's younger sister Cao Yangyang was busy pretending not to look while stealing glances.

If Cao Yangyang's eyes met his, Murong Zhuji would show her displeasure with a cold attitude and ruin the atmosphere, so his neck was sore from looking out the window to the left.

This is why women are absolutely detestable.

The only man present was in that state, and he missed the younger beast sage and the elder troublemaker Hwangbo to the point of wishing they were here instead.

\textit{Yes, if only that Sword Lunatic were here instead.}

\textit{It would be better to hear that bastard's half-sword talk.}

\textit{This is unbearable.}

\textit{Brother Changbin, you're the only- no.}

\textit{Come to think of it, with two women present, Brother Changbin would just pretend to be mute.}

Peng Daesan let out a deep sigh.

It was truly the worst time.

The only consolation was that they would arrive in Changyuan City tomorrow and meet up with the Murong Clan members.

Anyway, a small city's martial arts hall isn't big enough to accommodate three groups of Five Great Clans' members.

Moreover, it's not right for one martial arts hall to take all the precious guests, so they'll inevitably have to stay separately by clan.

Then both the Murong Clan and Cao Clan could be separated.

"Ah, Young Master! Look over there! Isn't the shape of that cloud strange? It's like, um, like something, anyway it's strange."

"Hmm, if I had to compare it to something, maybe a snake? A rope? To find uniqueness even in such ordinary forms, as expected, Sword Flower's observation skills-"

"Ah, Young Master! Look at those people passing by! Could they be lovers? Ah. I wish I could stroll on a spring day like that with a lover too. Isn't there anyone?"

-…You damn Jade Qilin…

Jade Qilin very slowly, firmly pressed down and brushed his bangs.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Murong Chengyi went for a night walk with his son.

However, at the place where the female beggar was supposed to be, there were just two layers of straw mats spread out.

"Ah. She must have gone to train first. It's this way."

And then he headed towards an empty lot that was secluded and rarely visited by people, which he called a training ground.

And that's when Murong Chengyi finally saw Qing.

"Oh my…"

Murong Chengyi let out a sigh.

How could Murong Chengyi, who was ranked among the Ten Great Masters under Heaven, fail to see through a mere face veil?

Under the moonlight, a peerless beauty was absorbed in a sword dance, a rare sight that no beauty under heaven could capture.

Honestly, his flirty daughter keeps saying she's the best among the Five Flowers of Zhongyuan whenever she gets the chance, but this completely ruins that.

Moreover, while the sword dance was familiar, drawing the forms of the common Yue Maiden Sword, the subtleties contained within changed moment by moment, showing she could freely handle sword imagery.

The subtleties of slowness and heaviness were admirable, but unfortunately, the subtleties of swiftness and illusion fell short.

However, she had mastered two of the four subtleties of swordsmanship.

Among the Transcendent Realm, there were plenty of useless fellows who couldn't even properly handle one subtlety like the Golden Mean.

They say Jianghu is vast, but how could such a talent be hiding in beggar's clothing?

However, when it came to sunset-colored True Qi burning through the night, even Murong Chengyi was reminded of a certain person.

"Ahem."

At Murong Chengyi's presence, Qing turned her head.

She had known the kid had come long ago, but only now noticed Murong Chengyi who had deliberately hidden his presence.

"Kid, if you've come, you should greet first, why just clear your throat? Ah. Are you Ajun's father?"

"Yes. I came out because it seems my son has been causing trouble. By the way, that's a familiar True Qi. Could it be the Zhu Xiang Heart Cleanse Mirror, the divine technique of the Divine Maiden Sect?"

If he's A-Jun's father, he must be the Murong Clan leader.

However, to Qing, he was more her friend's father than the Murong Clan leader, so she was very polite.

"Yes. I learned from Master Ximen Surin. However, due to circumstances, I didn't officially join the Divine Maiden Sect, so I'm Ximen Qing, an outer disciple of the Divine Maiden Sect."

"Ah! Senior Ximen Surin's!"

At the same time, Murong Chengyi ground his teeth inwardly.

\textit{That bastard Guard Bai.}

\textit{Her eyes are overflowing with pure spiritual energy to the point of spilling over, yet he talks about beggars?}

\textit{How can a guard with crossed eyes properly protect my son in the harsh Jianghu?}

Of course, Guard Bai, who lacks the ability to see through the face veil, might feel wronged.

And in front of Guard Bai, Qing was just lying sprawled out scratching her belly, not displaying the beauty etiquette of Ximen Surin's style.

"But why are you in such a state? As far as I know, Female Mad- no, Grand Matron senior wouldn't allow such an appearance."

"Ah. That. This girl had unavoidable circumstances that led to this decision. Um, could you please keep this a secret…?"

For a moment, the beauty's dignity cracked and a mischievous aspect peeked through, making Murong Chengyi laugh softly with the feeling of seeing his daughter.

"Alright. I know how senior's personality is. You must have your own reasons for hiding your identity, and this old man has needlessly made you reveal it."

"Not at all. As the father of a friend, what father in the world would just watch when told his son is associating with a beggar? Rather, I should tell you that the deception is beautiful."

\textit{With her manners and attitude so proper, isn't she truly a splendid female hero of Jianghu?}

Murong Chengyi smiled contentedly.

In fact, since the face completes the clothing, to Murong Chengyi who could see through the face veil, there was a certain charm even in the beggar-like clothing.

"Indeed. From what I see, your achievement is no ordinary thing. Looking at your limbs, it seems you've achieved Overhaul Rebirth, but unfortunately, you haven't crossed the barrier yet."

"Yes. To be honest, this girl had some careless complacency, but I'm keenly feeling how high that barrier is."

"Haha, since you've already glimpsed beyond it, you'll reach it soon. Hmm? By the way, how old are you?"

"I've just reached the age of beauty in my prime years."

Qing brazenly lied through her teeth, saying 'I'm twenty years old.'

If her master asked, Qing could lay down not just an iron plate but a diamond plate.

'Prime years' is a term used exclusively for women, referring to an age around twenty.

In Qing's homeland, many people completely misunderstood it to mean 'unknown age.'

"Oh my. Senior…"

Murong Chengyi swallowed his admiration.

They said the old monster Female Mad Dog had grown old and lost her energy with no news in Jianghu, but to think she was raising such a monster.

\textit{Come to think of it, I've heard something like this before.}

Didn't the Mount Hua Sect Leader give the ridiculous title of 'Divine Sword' to a Female Mad Dog's disciple, and was accused of going senile?

Seeing it in person, it was an achievement worthy of the title.

Moreover, she's just barely twenty years old!

With an achievement of peeking beyond the barrier and achieving Overhaul Rebirth, she was not only destined to be the future Zenith Among Women, but also a heavenly talent who could compete for the title of greatest under heaven with his son who had the Heavenly Martial Body.

"Indeed, she's a blessing to the orthodox faction. A-Jun, you've made a very good friend. To you as well, though my son is lacking, I entrust him to your care."

"What are you saying? Your son is already a magnificent young man, so there's no need for worry."

"Right. You said you have circumstances, so I didn't see you tonight, but if your schedule is to go to the Wulin Conference, my family members are staying at Sohua Sect, so feel free to come anytime if you want to go together."

Murong Chengyi took out a small wooden box from his bosom, opened it, and pulled out a guest token to hand to Qing.

Of course, it was a special token, and moreover, a special token with the clan leader's name.

With this, four of the Five Great Clans' unlimited free pass tokens were gathered in one person.

Except for the Zhuge Clan who hadn't given a guest token yet, she had one clan leader's guest token, two heir's guest tokens, and Qing was also a benefactor of the Tang Clan.

"Hmm. I've thoughtlessly intruded on friends hanging out together. I'll be on my way now."

"Please be careful on the dark night road."

"Haha, alright. You be careful too."

Murong Chengyi left for Sohuamun with a completely lightened heart.

But then a thought quietly arose.

\textit{By the way, if she's an outer disciple, isn't marriage possible?}

\textit{If two heavenly talents marry, wouldn't their child be born as the greatest of all time, surpassing even the supreme Celestial Martial Emperor senior?}

"This brat. He should have accepted when offered marriage."

Although having Female Mad Dog as an in-law is frightening.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And following the Black Store Leader and Ximen Surin, yet another person burning with anger.

"How dare those Black Store bastards. Ha."

Cui Liweng frowned deeply.

Suspicious guys tried to bribe with gold sycees and lure Jian Buxi while digging for information.

But the Xue Family Trading Company is the Hubei branch of the Heavenly Demon Divine Cult, constantly guarded by elite warriors dispatched from the Divine Cult's Covert Operations Division.

The guys who attempted bribery spilled the truth under the principles of the five elements (fire, water, thorns and clubs, iron tongs, earth), revealing that the Black Store bastards were behind it.

However, Cui Liweng wasn't such a peerless master that he could single-handedly raid the Black Store and slaughter them all.

But instead, he knew a group that would get angry together.

"Hey, young cult friend."

"Yes, elder."

"I'm sorry, but could you deliver this to the Divine Cult's Secret Pavilion? It's a very urgent matter, so please make it top priority."

Though his words were polite, it was actually just an order.

And with top priority, it meant a grueling schedule where messengers had to relay it desperately in a relay race to quickly reach the cult's leadership.

If there was one consolation, it might be that since the Divine Cult advanced into Zhongyuan and took over Jiuquan City beyond Jiayuguan in Gansu Province and established a Secret Pavilion estate, they didn't have to cross that terrible desert.

The Zigui contact point only needs to deliver it to the next city anyway, so there's no need to worry about the desert.

"Understood. I'll deliver it with top priority."

And so, Cui Liweng's letter raced towards the Heavenly Demon Divine Cult's Secret Pavilion.
