\chapter{Are You Acquainted With This Beggar? (6)}

"Oh my, our dear Flower Beggar."

"Why are you giving me all this…"

"I knew from the moment I first saw you that you had an extraordinary face. With twenty years of server experience, I could tell right away. Hehe."

It was a truly server-like line to talk about someone's face when they had never even seen it uncovered.

The server who had been strict, solemn, and serious changed.

Of course, it was partly because he lacked the courage to act like an adult when he knew she was a Wulin Master, but mostly because he was grateful to the benefactor who had protected his precious shop.

Surprisingly, a server is closer to a business partner than an employee. In fact, in the hierarchy of the restaurant, it goes owner, manager, server, then cook.

Of course, this can vary depending on years of experience and the shop.

But a server with twenty years of experience can be considered a co-owner.

"Don't give too much, just slowly give the exact difference. Generosity is good once or twice, but if it continues, a benefactor can become an enemy."

Not simply saying 'don't give' meant she intended to keep coming.

The server's expression was simply delighted.

The compensation given by the Virtuous Quartet of Qinghe was already more than enough to cover the broken furniture and the money customers had dined and dashed on.

On top of that, they told him to take the money and weapons collected from the corpses and sell them, so if you calculate it, several months' worth of income came in one day.

"Oh my, that is such a sad thing to say. Flower Beggar, you are a lifelong benefactor of Xiliang Restaurant."

Even while saying this, he inwardly admired her, fully agreeing with Qing's words.

The server's eyes began to fill with respect.

Full of wisdom in her words, and while being an incredible Wulin supreme master, practicing the way of non-possession with nothing to her name!

And then to mingle so freely with a lowly server, she is truly a righteous expert that only appears in storybooks, he thought.

It was a delusion that if someone heard, they would say it was as unbelievable as the sound of a dog eating grass.

But little do people know that dogs do, in fact, eat grass.

Usually, they eat it with a crisp sound as a digestive aid, and some unusual ones just like the taste of grass.

Just as the sound of a dog eating grass exists for the owner of a grass-eating dog, Qing was a proper female expert of Wulin to the grateful server.

Look at that majestic way of eating!

Could this be the heroic spirit of Xiang Ji when he charged in on a short horse and slaughtered Han's ten thousand soldiers?

Furthermore, seeing as how she drinks strong alcohol like water, she truly lacks nothing as a great hero of these plains under the heavens.

Moreover, her exposed chin and mouth are so beautiful, it's clear that the face behind the veil isn't hiding ugliness but must be that of a peerless beauty!

She's acting like a beggar, and even eating like a beggar, but still maintains her dignity!

The server, thoroughly affected by the eyes of one who views a benefactor, evaluated Qing's meal, or rather, her skill of stuffing food into her mouth and devouring it like a pig, in this way.

This is why they say human sentiment is frightening.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Zhang Enchai, the Black Store Association Leader, who had skimmed through the report detailing the damage, messed up his hair vigorously.

It wouldn't relieve his anger anyway, and it would only mess up his own hair, so it was a useless action.

It just showed how shitty his mood was.

"Guangdong, Jiangxi, Fujian, Zhejiang? Almost all of Yangzhou is gone? The Jin Prefecture's Un Clan's warriors, which were supposed to be destroyed, suddenly appeared and drove out customers and killed merchants?"

Yangzhou is an old term for the southeastern region of Zhongyuan. It was also called Jiangdong.

The northwestern region of Zhongyuan was also called Yangzhou, so it had two names to avoid confusion.

For reference, the Yangzhou in the northwest is also called Xiliang.

"The Black Store branches in every city were also destroyed."

"I know! I've already heard that!"

"What should we do now? Wouldn't it be better to cancel the bounty now?"

"Are you joking? If we back down now, how lightly will everyone take the Black Store? So that's how you want to play it, huh? Raise the bounty to twenty thousand gwan, dead or alive…"

-Association Leader, it's Yeonga.

At that moment, a subordinate interrupted.

"What is it, come in."

"Leader, this."

The subordinate approached respectfully, placed a scroll on the desk, and retreated.

"What's this?"

"Well, a box was delivered for you from Fujian…"

The method of sending letters or items to the Black Store Association Leader was simple.

If you give it to any Black Store branch, fence, butcher, loan shark, or related person addressed to "Black Store Association Leader," it would be delivered properly.

Of course, you should keep in mind that whether it's a letter or a box, subordinates open and check it before delivering.

The box from Fujian was also opened by subordinates to check if there was anything dangerous inside.

There was a terribly horrific thing inside.

A dog's body with a human head sewn on, and a letter placed in its mouth.

The head belonged to the Fujian Black Store Branch Manager.

"Ugh…"

Just hearing about it as horrifying enough.

The subordinate who actually opened the box immediately fainted and is still having nightmares.

Zhang Enchai unrolled the letter.

\begin{quote}
To the dear Black Store Association Leader,
\medskip

I apologize for harming the dog you cherish, so as a token of apology, I've attached the body of the bitch I was raising and returned it to you.

By the way, the name of the bitch I was raising was Zhang Enchai, so you've gained an ugly head of Zhang Enchai.

What should we do with this? Should we boil and eat it?

That was just a joke. It's a stray dog without an owner.

Looking at the wanted poster, it seems the person you're looking for isn't me, so I'm writing this letter.

I've attached my portrait on the next page.

Regarding the reliability of the portrait, you can check with the inspection officers of the Wulin Alliance.

Or you could check with the residents who used to live near the Un Clan's estate.

Please take proper action after verifying.
\medskip


P.S.: Since you put a ten thousand gwan bounty on an innocent woman, you'll accept this much damage with an open heart, right?

-Yun Yuanling, Clan Head of the not-yet-destroyed Jin Prefecture's Yun Clan」
\end{quote}

And on the back page, there was a well-drawn portrait of a beautiful woman with "Height: five chi four cun one fen" written on it.

"This dog-like…!"

Zhang Enchai crumpled up the letter and threw it.

At the same time, goosebumps rose all over his body.

\textit{How does she know my name?}

\textit{And what does she mean by the not-yet-destroyed Jin Prefecture's Yun Clan?}

It was a warning that she knew everything about his identity and what he was saying.

Along with the sentence about boiling and eating the head.

"Cancel, cancel the bounty!"

"Association Leader?"

"Damn it! It wasn't Yun Yuanling! From the start, it was another woman selling out the Jin Prefecture's Yun Clan and impersonating them! Damn it, I can't believe we didn't know this and had stirred up a hornet's nest for nothing."

He had messed up badly. The mother of all mess-ups if you will.

The only fortunate thing in this misfortune was that the letter didn't say 'You're dead now, so wash your neck clean and wait'.

In other words, it meant she would let it go if he withdrew the bounty.

"What kind of woman is she? It's twenty thousand gwan if we catch her. How do we find her? Weren't the others with her also impostors?"

"You mean Zhuge Lixian and Tang Lan-Ah? Those two are definitely themselves. Their faces are already widely known…"

"We can't touch the Five Noble Clans, and there was another woman with them, right? Did you put people on her? Where did she go now?"

"Well, after that, she went to the Dabie Mountains with her companions, took back the slave they were looking for, and returned to Zhumadian. After parting ways with the Five Noble Clans' young masters, she settled in the Xue Family Trading Company in Zigui County, Hubei Province, with the slave and an ironsmith called Old Man Ban."

"Xue Family Trading Company? What kind of place is it?"

"It's a trading company established by Xue Ganom-"

"Are you joking now? Of course it's established by Xue Ganom if it's called Xue Family Trading Company! What kind of person did you put on this that they couldn't even find out the owner's name and just called him Xue Ganom\footnote{Xue Ganom's name literally mean 'that bastard Xue'}?"

"…I'll take care of it. Anyway, it's a trading company that deals with various things, but its scale doesn't even reach that of a city."

An innocent victim was about to be created.

"So it's a hole-in-the-wall shop. If she's settled there, it should be easy to find out."

"However, since she visited the Divine Maiden Sect afterwards, she might be a woman with connections to the Divine Maiden Sect."

"What Divine Maiden Sect! What's with everyone flocking together, damn, of course they flock together. That's how those Orthodox Faction bastards are."

Zhang Enchai banged on the desk loudly.

"What will you do?"

"If we back down here, we'll really become the laughingstock of the world. Don't you know it's over if we're seen as a joke in this business? Announce a temporary withdrawal of the bounty, find out that bitch's identity first, then put up a bounty twice as high again. Xue Family Trading Company? Use as much gold as needed to bribe them, or send people, and bring that woman who's supposed to be her companion before me."

Xue Family Trading Company? Zigui County?

It seems to be a trading company set up in a thatched house in some countryside village I've never heard of, but if the Black Store gets involved, how dare such a trivial hole-in-the-wall shop defy us?

Zhang Enchai's eyes blazed with anger.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After seeing the wanted poster, Qing felt relieved.

So she drank plenty of alcohol, ate even more free food, and when her stomach was full for the first time in a while, she looked like someone might ask how many months pregnant she was.

She looked like one of those competitive eaters from her homeland, whose existence she couldn't understand.

One of Qing's favorite things to do is to eat until her stomach is about to burst and then lie down immediately.

A master who has undergone Overhaul Rebirth can do this.

Because the esophagus is strong, unless you're hit or poisoned, there's no reflux, so you don't get indigestion just from eating and lying down.

If asked to pick the best thing about Overhaul Rebirth, this was one of the advantages Qing could proudly mention.

The other two were not being afraid of periods and not getting sweaty between the breasts, thus making up the top three.

Not gaining weight no matter how much she ate was the case even before Overhaul Rebirth, so it seemed to just be her constitution.

At any rate, for once, food filled her up to her chin.

The server, impressed by her heroic demeanor, kept filling the table endlessly, allowing her to enjoy as much as she wanted, until Qing finally declared defeat, saying she had reached her limit.

Thanks to this, her expanded stomach was screaming to stop pushing in more, and it was perfect to lie down and enjoy that sensation.

So that's what Qing did.

The only person in the world who could stop Qing's unsightly behavior was her beloved master, Ximen Surin.

In other words, even when she wasn't pretending to be a beggar like now after leaving the Divine Maiden Sect, there was no one to stop this pitiful beast who would just lie down after eating.

Even before Overhaul Rebirth, Qing would lie on her left side because of indigestion.

Lying down on a straw mat like that, wearing thick warm cotton clothes, it was truly paradise.

Soon, a silky dream came.

How much time had passed?

"Sister, Beggar Sister."

"What…"

"It's me. Murong Jun."

"You came… If you came, then go…"

Qing waved her hand, drunk with sleep.

"Then I'll wait here…"

"Okay, stay right there and wait…"

Qing caught the dream that was about to fly away again.

Sleeping is good, but this state of being drunk with sleep, with the whole body languidly relaxed and the body warmly raised in temperature, is also a truly happy time.

How much time had passed? At any rate, since it was a nap, her mind naturally cleared as time passed.

Since she slept during the day and trained at night, even though it was the middle of the night, this was indeed a daytime nap.

If Ximen Surin knew, she would be torn between praising her for training regularly and lamenting how her disciple's behavior was becoming more pathetic day by day.

Qing sat up, put her hand inside her face veil to rub her eyes, and asked:

"Hmm. Murong Clan Kiddo, how long has it been?"

"Uh. Just a moment. The moon…"

Qing, half-awake, knew there was a motionless presence nearby.

But knowing that sweet dreams and a quickly clearing mind were coming, she just told that presence to wait a bit and left it alone.

Murong Jun looked at the moon, raised his fingers and wiggled them as if measuring its position, then answered brightly:

"I came about a shichen ago!"

"Huh?"

A shichen is two hours.

Feeling sorry, Qing blamed the innocent kid for no reason.

"Why did you foolishly wait for a whole shichen?"

"You told me to stay put and wait…"

And thus, it seems he had been standing still waiting without any sense.

"No, what? I was just going to lie down for a bit, you should have made yourself comfortable."

Qing scratched the back of her head.

She had just been lying down lazily, but how had so much time passed already?

They say enjoyable time passes quickly, the so-called theory of relativity. But was it always this fast?