\chapter{Are You Acquainted With This Beggar? (5)}

"They're human hunters. Something about a bounty. Oh my, everything's getting destroyed, destroyed, you hear. What do we do?"

The server stomped his feet anxiously.

Somehow, things seemed to be falling into place.

Qing first peeked out her eyes from behind the long table with a closed bottom to survey the situation.

It was a nine versus four fight.

But in terms of realm, the four were higher. Still, it wasn't exactly an example of how absolute realm is in Wulin from this fight.

There's no match for numbers, so the four were surrounded and sweating profusely.

Even masters need to be at least the Peak Realm to overturn numbers.

If the strongest was Late Stage First-Rate or Early Stage First-Rate and the rest were Second-Rate, the side with more numbers had the advantage.

"Ah, which side is that kid coughing up blood on? The four? The nine?"

"Originally, there were eleven."

The server must have been watching intently despite saying it was dangerous, as he pointed with a finger, showing a pair of knees under an overturned table.

"Oh my, it's a fight to the death then."

No wonder they were fighting so hard. With two already dead on the eleven's side, they had no choice but to go all out.

If the four had shown an overwhelming performance, it might be different, but they were constantly on the defensive, and even beasts don't hold back when they have the advantage.

"Hmm."

Soon the four would die, and they might take a few with them, but anyway, it was a victory for the side with more numbers.

However, while the Evil Karma of the many was quite colorful, the four were people leaning towards Righteous Karma.

Among them, the one who seemed to be the leader, the strong one, had as much as thirteen points.

"I'm going to use some chopsticks."

"Huh? What for?"

\textit{I was going to go out and clean up after the fight ended, but…}

Qing stood up abruptly and crossed her arms in front of her chest, with chopsticks somehow fitted between each finger joint.

It was a meaningless preparatory motion.

She just tried to imitate what Tang Lan-Ah did.

She somehow manages to throw so many at once.

Qing shook the chopsticks back onto the table, then grabbed them one by one and kept raising her arm to throw them.

The chopsticks, actually faster than arrows, stuck firmly into soft bellies, necks, and the backs of hands.

With various screams of Ack, Argh! Gak! spreading, the four didn't miss the opportunity and launched a Joint Attack Technique.

Three of them were perfectly in sync, but one much younger one seemed to be out of step and on the outside, making it a somewhat disappointing Joint Attack Technique.

How could it be a fight when a Peak-Transcending Master who could take down even Transcendent Realm Masters was throwing limb-piercing chopsticks?

"Wait! Stop! Spare that one!"

One chopstick flew and hit the sword of a Late Stage First-Rate master with a Tang!

And then the situation was over.

It was a total annihilation of the eleven's side, except for the two Qing deliberately spared because their Evil Karma was in the double digits.

The strongest among the four bowed politely to Qing.

"Thank you for your help, Senior. I am Cho Gaksan of the Qinghe Martial Hall, and though I'm embarrassed to say it, I'm known in Jianghu as the Virtuous Gale of Qinghe."

"Hmm. I'm just a passing beggar. In Xiliang Restaurant, I'm called the Flower Beggar."

Cho Gaksan's expression became subtle.

He couldn't tell if she was mocking him or just didn't want to reveal her identity because she had something covering her face.

At any rate, since you can't tell a woman's age just by her voice, Cho Gaksan thought that despite her strange appearance, she must be a senior in Jianghu.

There's more than just one or two eccentric people in Jianghu, after all.

"But, what's going on? Why are you fighting in someone else's business? How will you deal with all this damage? Can't you see the server uncle crying in sorrow?"

"Oh my… Sniff, how can we deal with all this… I haven't even paid off my debt to the owner yet…"

You don't deserve to be a server if you don't have this much tact.

The server pretended to wail loudly, lying on the table and making crying noises.

"Surely expert practitioners wouldn't harm innocent civilians and then ignore it, right?"

"O-Of course not! Here, um. It's not much, but please accept this…"

As Cho Gaksan took out silver sycees, Qing added.

"It really isn't much."

"Ahem, I was going to take out more. My hands are small, so I can't hold many at once…"

To Qing's eyes, it was a sufficiently large man's hand, so along with this unconvincing excuse, quite a pile of silver sycees accumulated in front.

Only then did Qing nod with a satisfied expression and ask:

"So, what's going on?"

"Ah. These are my brothers, we're wandering Jianghu doing good deeds. Because of that, though it's embarrassing, people in Jianghu have given us the excessive title of the Virtuous Quartet of Qinghe."

"Hmm? Virtuous Quartet of Qinghe? Why does that sound familiar?"

"Ah! You've heard of us too, Senior! Haha, how embarrassing…"

Cho Gaksan scratched the back of his head with a smug face.

\textit{Shouldn't it be the Virtuous Trio of Qinghe? It feels like there should be three.}\footnote{Chapter 2}

\textit{Why is that so? Is it because it reminds me of the Wonders of the Ancient World that don't exist yet?}

"So, what's going on- no, how many times do I have to ask?"

"Oh. I'm sorry. Actually, we were chasing a vicious wanted criminal, but these guys insisted on taking the wanted poster to look at it themselves. When we sternly admonished them that they couldn't do that, these unrighteous bastards drew their swords…"

Of course, we should hear the opinion of the eleven's side on this.

Judging by the resentful looks of the two still alive, it seemed they had something to say.

\textit{If you're so resentful, you should have lived righteously.}

As Qing turned her gaze away, the two drooped their heads dejectedly.

"A wanted poster. Could I take a look at it too?"

"Yes! Senior. Please wait a moment."

The Virtuous Quartet of Qinghe busily searched the corpses, then soon found and held out a folded piece of paper.

When Qing unfolded it, there was a woman drawn in a realistic style unsuited to Chinese painting, who seemed to be beautiful but not quite.

Unfortunately, wanted posters only work for faces with some distinctive features; it's difficult to depict just a beautiful person even with modern production methods from Qing's homeland.

\begin{quote}
[Black Store Wanted Worldwide: Yun Yuanling of the Jin Prefecture's Un Clan.]
\medskip

This criminal is widely wanted for torturing and brutally murdering an innocent merchant before fleeing.

Five hundred gwan for a part that can confirm death

Ten thousand gwan if delivered alive

Two thousand gwan deducted for each missing limb
\medskip

Characteristics:

Realm estimated to be Transcendent

Beauty comparable to the Greatest Beauty Under Heaven

Tall, but not reaching six chi

However, has a large build with a thick body and much flesh
\end{quote}

"What is this?"

\textit{Do I look like a pig or something?}

Originally, when a woman with large breasts wears thick cotton clothes, it stretches out to the largest circumference like a single piece, making the body look particularly large.

This is why large breasts are disliked in Zhongyuan beauty standards, because they ruin one's figure by making clothes look unattractive and fat.

At any rate, after confirming the wanted poster, Qing felt relieved.

\textit{What the heck? How can they find me with this?}

At that time, the Virtuous Quartet of Qinghe were also looking at the wanted poster.

The human hunters' gang had torn off more than one wanted poster.

It was common practice for human hunters to tear off wanted posters to monopolize them and hinder competitors.

The Virtuous Quartet of Qinghe looked at Qing with a subtle expression.

Estimated Transcendent Realm. Covered face.

Tall. Large build with a thick body and much flesh.

Moreover, not only Qing's breasts but also her hips greatly exceeded the average, so wearing thick clothes made her body look very thick in a straight line.

"Um, Senior?"

"What?"

"Perhaps, um, never mind."

Cho Gaksan quickly changed his words.

Asking a woman with a covered face to show her face was a rudeness that could lead to bloodshed even if it seemed strange.

Qing felt a pang of realization when she saw another wanted poster in Cho Gaksan's hand.

\textit{Ah. They can recognize me with this? Is it because of the height?}

\textit{But do I really look like a pig?}

\textit{By the way, why am I getting so angry?}

\textit{What's wrong with looking a bit thick?}

No matter how much she tried to think like that, somehow her insides kept boiling and wouldn't calm down at all.

\textit{Wow, I'm really pissed off.}

\textit{Which bastard made a wanted poster like this?}

Due to the chilling aura leaking from Qing, Cho Gaksan swallowed hard and spoke with a trembling voice.

"Um… Senior?"

"Ah. Right. I know what you're thinking, but I'm actually slim, you know? Here, look at this."

Qing grabbed the hem of her clothes at her waist and rolled it up tightly.

As her monstrous strength rolled up the fabric at her waist almost to vacuum-pack levels, her width was reduced to about half.

"Ah! What an amazing- ahem. I couldn't tell because you were wearing such thick clothes."

"It's because of the clothes, right?"

"Yes, winter clothes are all like that, aren't they? I am truly ashamed. I apologize."

Cho Gaksan, having completely dispelled his doubts at the good sight, showed his crown along with his brothers.

Perhaps because of this, Qing's anger also melted away.

What can you do when they apologize so sincerely?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The black market is held separately in each administrative city, with two places in the vast Sichuan land opening in the east-west or north-south, while one place opens in each province.

Within the city, it changes location every five days or so, so it wouldn't be far off to call it an irregular five-day night market.

Anyway, black-clad people suddenly swarmed into the black markets of Fujian Province and its neighbors, Guangdong Province, Jiangxi Province, and Zhejiang Province.

Among them, there wasn't a single low-level person, and even many invulnerable monsters whose bodies weren't harmed by blades swarmed.

"This is the Yun Clan of the Jin Prefecture's event! We're only punishing the unrighteous who dared to threaten our Clan Head! Guests should leave with their weapons held above their heads with both hands!"

"We're only punishing the black market! Innocent guests should leave!"

Since Yun Yuanling wasn't a fool, there was no reason to unnecessarily create enmity by cutting down even customers.

Therefore, she specifically targeted only the black market and merchants with a justification.

Merchants wouldn't have brought weapons with all their luggage, and if some did, well, they were lucky.

Then the scared martial artists who used blades, commonly called Blade Path practitioners, shouted:

"What about those who practice fist techniques?"

"You useless fools! Why do you stupidly, foolishly, and stubbornly just swing your arms and legs when there are good weapons? You are idiots who need to test whether your arm or a sword gets cut when they clash! Those who practice fist techniques should raise both hands and keep shouting the names of the fist techniques you've learned!"

Then techniques with animal names like "Fierce Tiger Pounce" and "Crane Descends from Waterfall" rang out loudly.

Then this time, ordinary civilians who just came to look around shouted:

"Oh my, noble being! I am not a martial artist!"

"Tsk. Then shout your place of origin and name! The Un Clan's blade will avoid you then!"

"I am Wang Junyeong from Sihung, Guangdong Province! I am Wang Junyeong from Sihung, Guangdong Province! I am Wang Junyeong from Sihung, Guangdong Province!"

Thanks to this, amidst the clanging of blades and screams, the sound of animals stupidly shouting names rose high, and with untimely self-introductions added on top, it became a complete pandemonium.

Through the burning black market, a sickly woman who didn't fit in moved with careful steps.

As Yun Yuanling burst into the central office of the black market like this, the Guangdong Black Store Branch Manager exclaimed in shock:

"Wasn't the Jin Prefecture's Un Clan destroyed…!"

"My, my, what a hurtful thing to say. I am the Jin Prefecture's Yun Clan. Oh my, is this my wanted poster? Let's see how prettily they've drawn me."

Yun Yuanling picked up the wanted poster.

Yun Yuanling's expression, which always had a faint smile, became similar to Qing's face when hearing difficult words.

Someone watching might say it was an expression that made question marks pop up all over.

"Oh…? Who on earth is this?"

"Isn't that bitch Yun Yuanling!"

"This is supposed to be Yun Yuanling? But who could this be. Six chi…? Xinpa, do I look that big to you?"

Then, Poof, a snow-white hand shot out through the Branch Manager's chest.

In the hand that was dripping rather than stained with blood, a human heart was neatly placed.

Soon, the Branch Manager, whose heart was taken, collapsed, and Xinpa threw the heart to Yun Yuanling while sneering.

"Heng. Looks like the bitch who acted so smart got properly fooled. Just look at you. It's obvious it's an impostor. Anyone can impersonate a ruined clan, right?"

"Ah. My material."

Yun Yuanling clumsily caught the heart flying in a parabola, barely managing to grab it, and put it in the pouch at her waist with a troubled smile.

"How dare they impersonate me. They must be quite bold. Hmm. A beauty comparable to the Greatest Beauty Under Heaven. Could it be one of the Five Flowers of Zhongyuan?"

"Unless the Black Store bastards' eyes are crossed, they wouldn't have caused this fuss without recognizing one of the Five Flowers of Zhongyuan."

"That's true… Then who could it be…"

At that moment, someone flashed through her mind.

Yun Yuanling's eyes curved prettily with a tinge of longing.

"Qing'er isn't that much of a beauty, though…"

"Hm? What are you saying?"

"My, my. Eavesdropping on my soliloquy. You really have a nasty personality, don't you?"

At this, the White Hand Witch snorted.

"Hearing this from the nastiest bitch under heaven truly makes me feel dirty. Hmph. What will you do now?"

"The Black Store people were just deceived. Shall we withdraw now?"

"We've wronged the Black Store bastards. We've thoroughly crushed them without knowing they were deceived."

"What? Oh my, hic, Xinpa, what, kind of, hehe, joke, hehe, this time. Ha, interes- Kyahaha…"

Yun Yuanling couldn't hold back and burst into loud laughter, bending at the waist.

After laughing heartily for a while, Yun Yuanling wiped away tears and barely managed to continue speaking while rubbing her stomach that hurt from laughing too much.

"That was the funniest joke Xinpa has ever made. Then, does Xinpa feel sorry every time you swat a mosquito or fly? Ah, shall we build a shrine to commemorate vermin together? So that Xinpa can feel at ease."

At this, Xinpa's expression soured.