\chapter{Are You Acquainted With This Beggar? (13)}

Cao Haocai, who was proudly guarding the alley against the women, was shocked.

Peng Daesan appeared, holding Qing tightly in his arms.

Of course, the women also screamed.

"Brother? Why are you coming out holding her so preciously? Was it that good?"

Peng Daesan answered with a grin.

In fact, it wasn't for Cao Haocai, but for the women who had created a scene of tears and great wailing to hear.

Even the people of a certain country in Qing's homeland when their leader passed away probably weren't this heartbroken.

"It was absolute paradise. I've realized now that dirty, smelly beggar women are my type. I'm going to get a room and enjoy all night long, and if she agrees, I might even take her as my wife."

At this, Qing pretended to be shy, burying her face and whispering close to his ear.

-What? Dirty, smelly beggar woman? A person can go without bathing sometimes, do you have to be so picky?

Peng Daesan pretended not to hear.

With Peng Daesan's shocking public declaration, hell descended in the middle of the city.

Mainly in terms of sound.

If you were to combine the sounds of eternally burning sinners crying, screaming, or cursing and wailing in resentment, it would be exactly like the sounds heard here now.

Along with this, there were people fainting left and right, and some were even showing symptoms of seizures like epilepsy patients due to severe shock.

Peng Daesan listened, saw, and felt the screams and collapsing figures with enjoyment, and a refreshing smile born of sincerity appeared on his face.

It was an incredibly satisfying sight, washing away a bit of his lifelong resentment.

Seeing that relieved smile, Cao Haocai clicked his tongue.

"Then there's nothing to be done. I can't be a bad older brother who covets his sister-in-law. Hmm. Have a good time. And miss, um, since it's Peng brother's first experience, he might be clumsy, but he'll follow instructions well, so don't think it's frustrating and please enjoy your cloud and rain pleasure- Hey! This bastard is trying to kick his brother!?"

"Please stop saying unnecessary things. I beg you."

Qing's eyes flashed.

How could she endure hearing this?

-Aha. A virgin, pure and innocent? Our San was such a pure San? Ooh, San who kept his chastity. I really praise you. Cool. The best. Pure San, should we change your title now? How about Pure God? Too obvious? Then Boy God? Innocent God? Pure God?

At this, Peng Daesan gritted his teeth.

A wave of deep regret washed over him belatedly.

Right, she was this kind of woman.

Why did he insist on holding her back and volunteer for this humiliation when he could have just said to meet later at the Wulin Conference?

-If you don't like God, how about Dao God? Hmm, somehow it sounds like you might gamble, so how about Dao King? Pure Dao King? Boy Dao King? Innocent Dao King? Pure Dao King? Come on, just say the word, I'll shout it loud and clear and stick you with a cool title.

"Stop it."

-Alright, I'll stop. There you go lowering your voice again. Should we add bass too? Pure Bass Peng Daesan, Bass Boy- oh, doesn't Bass Boy sound good?

Peng Daesan ground his teeth, Grit Grit.

After that, they broke through the chaotic scene and went straight into an inn to get a room.

Peng Daesan and Qing, who had entered the inn, soaked a towel in hot water and then wrung it out roughly.

Qing rubbed her face vigorously with the damp towel until it made a scrubbing sound, then tossed it into the waste bucket and picked up another towel.

Originally, this is the order of bathing: first wipe off some dirt with a wet towel, then soak the body in the bathtub.

"Wow, so refreshing. When is the bath water coming? Wow, my heart is pounding at the thought of taking a bath after so long. This is why I don't bathe."

"What kind of dog-like talk is that again."

"Why, it's really amazing when you bathe after not bathing for a while. Especially when washing your hair. When it's all grimy and you pour hot water over it, lather it up and gently scratch your scalp, wow, just, kyaa. Really, for a moment your legs go weak and there's this tingling sensation that shoots up from behind your knees, wow, that pleasure is, there's no need for men and women to copulate. I'd be fully satisfied bathing just once a month."

"…What kind of dog-like talk is this, do you usually not bathe?"

"I bathe when there's a chance?"

However, it meant that if there wasn't a chance, she wouldn't go out of her way to create one to bathe.

It was private information he never wanted to know.

Peng Daesan frowned.

"I don't understand. How can a person sleep without bathing? Just thinking about the bed getting dirty, it's absolutely, hoo, terrible."

"Well, San is a young master, so you always had the chance to bathe. And, if I can strip my upper body at a well and just cover the lower part to pour water over myself, I do that too."

Qing said this while continuing to move her hands.

The staff who saw the flower beggar had piled up towels like a mountain.

She kept wiping her hands, arms, feet, and neck, and the dirty towels kept flying into the waste bucket one after another.

"Ah. I'm going to wipe my body now, so can you turn around? No, should I turn?"

"I'll turn."

Peng Daesan turned his chair to face the wall.

And then in his ears, the sound of fabric brushing and slipping off, seuruk sareuruk.

In Qing's homeland, some poet described this as the sound of snow falling and piling up, but in fact, for a man, there's no sound more erotic than this in the world.

For reference, in Zhongyuan, unlike modern times, there are no other media, so it's an era where only aesthetically excellent but not at all sexually stimulating spring flower collections exist.

Peng Daesan's face turned bright red.

However, he soon regained his original complexion at the following sound.

"Kyaaa, this is truly otherworldly refreshment. It's completely out of this world refreshing. It's amazing, makes life worth living. This is what I live for."

"What's with that middle-aged-like talk…"

"This is how you make it feel good, you know? So what kind of sound does San make? You don't say things like ‘My face reflected in the water is art today,' do you?"

"I don't particularly make any sound."

"Eh, how boring."

At the same time, Peng Daesan thought.

What on earth is this conversation without any tension?

How can she show no sign of hesitation while in a room with a man, and chat so comfortably just because he turned his back?

Of course, Peng Daesan knows the reason.

She doesn't think of him as a man at all, considering him completely harmless.

In fact, that's why he was able to associate with Qing.

If Qing had shown even a hint of romantic feelings, he would have pushed her away in disgust.

But still.

How can she have absolutely no sense of crisis?

How can she trust a man and casually throw off her clothes in a room in the harsh Jianghu?

Of course, Peng Daesan himself didn't care because to him, she was a woman-like non-woman, an honorary man, with whom he had built a friendship based on pure platonic feelings, almost like a same-sex friend.

\textit{Does she just trust anyone who calls themselves a friend?}

\textit{Well, like that Sword Lunatic.}

Peng Daesan didn't know that he was making a stiff, hardened expression.

If Peng Chaolei had seen it, she would have asked why her brother looked so angry.

"Do you usually take off your clothes so carelessly?"

"Huh? Usually when I'm at the Divine Maiden Sect, yes? Even when sleeping, if I wear anything it's uncomfortable and I can't sleep."

This was the answer from Qing who had slept all day in beggar clothes under the sun.

Peng Daesan was dumbfounded.

\textit{What kind of answer is this again?}

\textit{But the Divine Maiden Sect is a Daoist temple that forbids men, so women showing their bodies to each other wouldn't be something to be concerned about, right?}

\textit{But it's uncomfortable to wear anything when sleeping? Then when sleeping…}

Suddenly, Qing's aggrieved voice interrupted.

"What? Why are you lowering your voice?"

"I didn't."

"There was a hint of it being lowered."

"It's not."

"Strange. It definitely went down about a semitone."

And then Peng Daesan smiled a twisted smile while facing the wall.

"If I turn around now, I'll see everything, right?"

"Why are you suddenly being spiteful? Did I do something wrong- ahem, well, the rumor about sleeping with a beggar, you said it was good too. I was a bit insensitive. I'm really sorry…"

Qing apologized dejectedly.

If she feels wronged she doesn't hold back, but if she's sorry, she's just honestly sorry, that's her straightforward nature.

At this, Peng Daesan came to his senses.

"No, it was a joke, just a joke."

"What, it was a joke? It doesn't seem like a joke because you feel guilty. I'll take it as a joke too, then. San! Do you want to see my body? Have you finally opened your eyes to the mystery of the female body? Should I show you?"

"You shouldn't say such things even as a joke. Where on earth did you learn to make such ill-mannered jokes?"

Peng Daesan became serious again.

This time, Qing answered as if she wouldn't be fooled.

"You can't play along with this. It's supposed to be the scene where I'm wrapped in a blanket when you turn around after the provocation. So if you're going to turn around, give a warning and count. You have to give me time to wrap myself in the blanket."

At this, Peng Daesan sighed while facing the wall.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was April, when spring was in full bloom.

However, the spring of Wang, the gate guard, was cold due to Cho who had come on duty with him.

"Damn bastard. My head still hurts because of you, shit. I'd like a cup of cloudy rice wine."

"The fool who gets fooled is the idiot. Why would the flower beggar keep being a beggar after receiving such payment? She'd buy a brothel and become a madam."

"I heard you were also fooled, beaten, and even pissed yourself? Oh spilled everything."

"Ahem. Still better than that bastard Oh."

Oh apparently went to find the flower beggar with just twenty wen, and was beaten four times for asking if she was trying to buy him with this, they say.

He had one foot in the Yellow Springs after being hit once.

After being beaten four times, he's likely to have half of next month's salary cut for being absent for a week.

Because military law is strict, if you're absent, not only do you lose that day's pay, but you also have to pay one and a half times more as a fine.

"Ah, look there. Isn't that the flower beggar?"

"I heard the flower beggar slept with the Jade Qilin yesterday, why is she coming out? But that height and those breasts. Three swords. Isn't it the flower beggar?"

Qing had wrapped the twin daos and Fushen-di in dirty cloth after the sword thief incident.

To others, it looked like three swords.

"Oh yes. We caught her good. If we strip her naked for inspection and make her stand all day… Oh, it's not the flower beggar."

"Oh my, it's a fairy, it's a fairy."

As Qing got closer, the gate guards changed their words.

It was partly because she was a peerless beauty who could appear in a fairy painting, and partly because she was displaying Ximen Surin-style beauty walking, with every graceful movement exuding dignity.

As Qing was about to pass through the city gate with such an elegant gait, her eyes met with eyes that were following her face with a completely dazed expression.

Qing slightly bowed her head in greeting and walked inside, disappearing.

Even after that, Wang, who had been standing there in a daze for a while, suddenly leaned his spear against the city gate.

"What? Where are you going?"

"To the latrine. I can't take it. I need to pull one out while her beauty is still fresh in my mind. What- Hey! Cho!"

"Haha, I'm first, kuhaha!"

This was the moment when Ximen Qing, the outer disciple of the Divine Maiden Sect, (officially) visited Changyuan City for the first time.