\chapter{Black Market Commotion (2)}

Wangfujing was originally a famous wealthy district in Beijing.

Or it referred to the street selling snacks in the black market.

Only the Black Store Manager would know why they specifically named the snack-selling street Wangfujing.

It was also a specialty of the black market, as hungry customers gathered due to the night-time nature of the black market.

And because they sold all kinds of bizarre foods.

Giant centipedes, scorpions, water bugs, flying squirrels fried with limbs and wings spread, palm-sized spiders, various long caterpillars, unknown insects, etc.

Of course, there were certain items that sold among them.

It was silkworm pupae called 'heavenly worms', a common snack seen anywhere in Zhongyuan.

It's the same silkworm pupae that Koreans enjoy.

Instead, the Chinese people ate them after they had become "king pupae" that had evolved further than regular pupae, so they were a bit bigger than Korean silkworm pupae.

They were about the size of a woman's thumb.

The food at Wangfujing was not to be eaten carelessly because everything from the source of ingredients to freshness was unreliable.

But silkworm pupae were a verified clean snack as they weren't adulterated with anything and were raised through sericulture.

The group each held a skewer in their hands amicably.

Even the Namen Sect martial artist Namen held a skewer with a sour expression, but he couldn't take his eyes off it and swallowed hard, seeming to like it.

"Fried centipedes… Do people actually eat such things?"

"They don't. Ptui."

"But it says it's a specialty? Ptui."

It wasn't the sound of spatting in disgust, but of spitting out the tough skin.

The basic way to eat silkworm pupae snacks is to eat only the savory insides and either chew or spit out the skin according to preference.

For reference, Tang Lan-Ah, the young lady from a noble family, couldn't be satisfied with just one silkworm pupae skewer, so she held two, one in each hand.

Sichuan's specialty isn't mala but silk, and surprisingly and mysteriously, silkworm pupae are left after weaving silk.

"It's unexpected. I didn't know you'd offer food to that lowlife too. I thought someone like you, Sister, would put a bowl on the ground and fill it with spoiled rice, telling him to eat like a dog."

Zhuge Lixian urgently pointed to one side.

It was a man with long, dry hair tied back tightly, including his bangs, somehow giving a poor impression with a roughly shaved, dirty dark face.

He had the appearance of a common wandering swordsman that made you feel like you'd seen him somewhere before.

Originally, wandering swordsmen-sword-for-hire types generally had their hair tied back, were actually poor, and shaved or didn't shave their beards as they pleased.

His realm seems to just barely reach the Transcendent?

He was above the Peak Realm, but it was ambiguous to call him Transcendent, so he probably hadn't achieved it long ago.

For a wandering swordsman, it was an exceptionally high realm…

The Transcendent wandering swordsman hesitated for a while holding a spider skewer, then carefully brought one leg to his mouth.

"Ugh." "Eugh." "Urk." "Ugh."

All four in the group groaned simultaneously.

In fact, not just Qing's group, but everyone on the street was either openly watching or glancing at him.

The phenomenon of so many people frowning at the same time occurred!

The wandering swordsman's expression was subtle.

It seemed it wasn't entirely unpalatable.

Perhaps encouraged by this, he bit into the body and chewed then-

"Bleurgh!"

He immediately bent over and brought out what he had stored in his stomach, a moment of reversal when what should not have risen came up.

The wandering swordsman, who had barely composed himself, pointed angrily at the stall owner.

"A-Are you crazy! You sell this kind of thing for three silver pieces?"

"Didn't you buy it yourself, customer? Did someone threaten you to buy and eat it? You eat it yourself and then yell at me."

"Wh-What! Do you know who I am! I am Tael Yaksha Yik Taikong!"

"Whether you're Tael Yaksha or Dog Yaksha, what do I care? If you're not buying, get lost."

It was an amazing sight.

A mere stall owner was talking back to a Transcendent Realm martial artist.

At this moment, Tael Yaksha, his face turned red, grabbed his sword hilt.

"What, you want to draw out your sword? You'll cut down a Black Store member in the black market? Go ahead. Try cutting me."

At this, Tael Yaksha hesitated, then turned away with trembling hands.

And just as he was about to brush past with angry steps, it happened.

Qing asked Zhuge Lixian in a voice loud enough to be heard:

"We can't touch such a vicious merchant? But is it okay to touch them when it's not in the black market? How about watching where they go when it's over and then swish-slash?"

"Hmm. Of course they'd want to protect Black Store members, but they can't escort each and every member home. Once dawn passes and the Black Store closes, the black market will withdraw completely."

"But won't there be consequences later? Like sending assassins because someone messed with their people?"

"Even from the black market's perspective, rude and unfriendly merchant bastards are a headache. Especially if they're rude enough to a Transcendent Realm Master, how much worse must they be to other customers? They won't care even if they die on the street."

It was a conversation meant to be overheard.

Tael Yaksha stopped in his tracks.

Then he bowed his head to Qing and Zhuge Lixian, turned back, and sat down on the opposite side of the street from the stall, crossing his arms.

The unscrupulous merchant selling insects noticeably became uneasy.

Probably by tomorrow, one unscrupulous merchant who was unfriendly and had accumulated evil deeds through unknown side jobs would meet his death anniversary without fail.

\textit{But by the way, Tael Yaksha… Doesn't that sound familiar?}

Of course, Qing didn't hold back when she was curious.

"Tael Yaksha? Is he famous?"

"Sister, how could a Late Stage Peak Realm wandering swordsman not be famous? Tael Yaksha is counted among the top Masters among wandering swordsmen."

"Ah, maybe I heard about him when I was briefly a wandering swordsman? Anyway, he'll become more famous from now on. I wouldn't have been able to tell with a First-Rate's discernment, but this Peak-Transcending Ximen Qing sees that he's entered the Early Stage Transcendent Realm, you know?"

"Amazing. Tael Yaksha is amazing, and Sister's arrogance is amazing. Perhaps he might be called the Wandering King in the future."

At this, Tang Lan-Ah, who was alternately eating one silkworm pupae from each hand, asked with wide eyes:

"What? You, you were a wandering swordsman?"

"In the past. After trying both, I found there's not much difference between a beggar and a wandering swordsman. Both have no money, are dirty, suffer from the heat in summer and are miserable from the cold in winter. People think you'll do anything if they buy you food. They kinda look at you with fearful yet dismissive eyes? With pitying gazes."

After that, Qing thought to herself-

\textit{Huh? Isn't that kinda like a graduate student?}

Qing didn't think much of it, but for Tang Lan-Ah listening, it was another tale of hardship that sent chills down her spine.

"Uh, um… Sorry. Want some skewers?"

"No, why are you giving me what you were eating? Am I a beggar?"

Qing said as she took the skewer with two left.

And then, along with the unique dining area of the night market with tables spread out, all kinds of restaurants were laid out in a circle.

"Zhuge, what on earth is ‘nameless meat'?"

"It's things so cheap they're not eaten. Smelly beasts like yellow weasels, wildcats, raccoon dogs."

In order, they were ferrets, wildcats, and raccoon dogs.

"They really eat everything with four legs…"

"They eat things without legs too. Those rolled up over there are snakes, and the ones spread out are prepared snakes. The rolled up ones next to them look like snakes but are goat penises, ahem, excuse me, Sister."

"Wow, the length is even longer than snakes. Could that be."

"I hear it doesn't taste good. Even though they say it's good for men, it's not popular enough."

The source was unknown, the hygiene and precision of the butchering were unknown, and even the taste was bad as they just sprinkled some seasoning and cooked it over fire.

Qing obediently gave up and passed through Wangfujing Street.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As they went deeper, they were said to deal with more secret items, but there was no classification for displaying goods, so all kinds of odds and ends came out.

To Qing, it looked just like a flea market.

When they came to an area selling poisons, Tang Lan-Ah said she wanted to look around for a bit and stayed behind, and Zhuge Lixian also couldn't tear himself away from the antiques section, so Qing told him to go ahead and look around.

In fact, Zhuge Lixian had emphasized and warned her strongly, so she was just thinking of politely inquiring around in the black market.

It's not strange to feel like you're on a trip if you don't think there will be any knife fights or ominous events, but still.

\textit{These guys.}

\textit{We came to get Old Man Ban's grandson, not to sightsee.}

"Hey there, beautiful one, my goodness, you must be the incarnation of a Fairy! The Greatest Beauty Under Heaven was here! Come over here and take a look at some martial arts manuals!"

"Oh, they're selling martial arts manuals. Sworn Sister, let's go take a look."

"Yes! There might be some peerless martial arts!"

"There's no way something like that would be here…"

Namen added a word to that.

"Oh? Looks like you've found your voice?"

"Huk."

When Qing frowned at him once, Namen closed his mouth with an expression like he was about to stop breathing.

It was because Qing's beauty was dizzying and harmful.

Understanding this as him being scared, Qing proudly approached the martial arts manual merchant.

"Oh! The True Arts of Yang! Huh? Was that the name?"

Qing picked up a book just in case, but the Martial Arts Window was quiet, so it was clearly fake.

Then the merchant who had laid out books spoke.

"Please don't open it, beautiful customer. If you open it, you have to buy it."

"I'm not looking. Besides, how can martial arts manuals be so clean? They should be tattered and worn to have the right feel."

"That's because we've copied them out for customers to see better."

\textit{Isn't that not allowed?}

Qing tilted her head and picked up each martial arts manual one by one.

Tai Chi Control Sword, Twenty-Seven Moves of the Cherry Blossom, Heaven-Rending Dao, Thousand Treasure Divine Fist, King Zhou's Heart Cleansing Scripture, Wudang Sleep Rape, and so on…

With titles that each seemed to have a screw loose, and books that were completely new and shiny, it was hard to believe.

"Mister Merchant, do these actually sell?"

"They sell quite well, yong."

"This mister's way of speaking is a bit…"

"Unique, isn't it, yong? I'm the famous Jeon Daeyong, the Jack-Of-All-Trades Merchant, yong."

"Jack-Of-All-Trades Merchant!"

Qing shouted.

If Zhuge Lixian had been there, she felt he would have shouted, so she felt a sense of duty.

Because of the attention drawn, Qing first confirmed the facts.

"Hmm. Are you a famous person?"

"No, I just made it up, yong. How can a person's name be Jeon Daeyong, yong? That doesn't make sense, yong."

"Hehehe, you're an interesting person."

Qing giggled as she answered.

This really made it feel like she had come to a real market.

Just like how she used to take each new lover to see the truly unbelievable and bizarre merchants all gathered in one place.

\textit{Ah. Those were good times.}

\textit{Thinking about it makes me feel a bit lonely…}

As if the claim that they sold quite well wasn't a lie, the stall that had been empty when calling Qing was now crowded with other customers.

"Ahem, shopkeeper, give me one of these. How much?"

"How much have you found out, yong?"

"…?"

"Divine Arts naturally have predetermined owners, so isn't it the law that those who know their value should have them, yong?"

"Usually, the seller sets the price for goods…"

"You'll have to give at least two gold sycees, yong. Too expensive, yong? No, how cheap do you consider the Wudang Sect's, no, all of Jianghu's best Qinggong, yong? What? You won't buy, yong? Hey, customer, do you think I'm doing this because I have nothing better to do, yong? Oh, I'm getting angry, yong. Do you want to be a customer or not, yong?"

As he showed his momentum like this… \textit{Wow, what's this, Unrestrained Realm?}

\textit{Why is an Unrestrained Realm Master selling fake books?}

\textit{Seriously, everyone and their dog is in the Unrestrained Realm these days.}

In the end, the poor customer was forced to buy the clearly fake Wudang Sleep Rape manual for two gold sycees.

"I'm telling you in advance, I'm just here to look around, okay?"

"Oh, that's fine, yong. Looking is free for beauties, yong. Hmm, will you look around for one more ke if I give you this, yong?"

The self-proclaimed Jeon Daeyong held out two coins.

Only then did Qing realize she had been had.

This mister was using people as signboards.

Since all kinds of gazes followed her when she took off her face veil, just being held at the stall was almost like a flashing advertisement board.

In reality, it was the sight of a peerlessly beautiful woman carrying a sword looking at things with a serious expression.

So everyone couldn't help but be tempted, thinking maybe there really was something there.

Qing, unable to refuse pocket money given by an Unrestrained Realm Master, obediently accepted the coins.

Of course, since Jeon Daeyong had no particular hostility, Qing's mouth, which had taken a stance, didn't move.

"You just earned two gold sycees and you're trying to get away with giving just two coins? Wow, you're stingy. So stingy that it stings like saltwater."

"That's fine too, yong. Next time I'll have to call myself the Coastal King of Salt Fields, yong."

"Coastal King of Salt Fields!"

"…Do you really have to shout that, yong?"

"I heard this is the polite thing to do?"

"I guess so, yong? Well, it's nice to meet a polite customer, yong. I can't give you more money, but you can look through the books for one ke, yong."

"It's not like there's any value in looking anyway."

Still, Qing picked up and looked at each and every book.

Suddenly, the Martial Arts Window flashed.

"Oing?"

It was flashing, saying a new gold-colored Hand Technique called Shadowless Divine Hand had been registered.

Qing didn't know, but this was actually the moment to shout exclamations loud enough to shake heaven and earth.

'My goodness!!! Shadowless Divine Hand!!!! The Divine Thief!!!!!' Like that.

The Shadowless Divine Hand was the exclusive martial art of the legendary one-man thief, the Shadowless Divine Thief!

But how would Qing possibly know that?