\chapter{Black Market Commotion (3)}

"Customer? What's wrong, yong?"

"Oh, it's nothing."

Qing gently put down the book.

It was extremely suspicious that not just any other color, but a Gold Martial Art suddenly appeared.

The secret manual merchant, Divine Thief, narrowed his eyes.

But since his eyes were already narrow to begin with, narrowing them further didn't make any meaningful change that others would notice.

It was suspicious how someone who had been carelessly skimming titles and tossing books aside suddenly carefully put one down with proper posture.

"Hmm? What's wrong, yong? Ah, Shadowless Spring Wind, yong. To recognize this, you have an amazing eye, yong!"

"Recognize what? I didn't even open it."

"Did you notice something, yong? It's the legendary erotic art1 collection by Master Artist Geum, yong. You recognized it, yong! Here, take a look at this, yong. How is it, isn't it lewd, yong?"

The Divine Thief opened the book and thrust it forward.

An explicit depiction of an intense lovemaking scene between intertwined men and women was spread across both pages.

The Divine Thief expected one of two reactions.

Either seriously looking for the mantra, or blushing and not knowing what to do out of embarrassment.

But Qing's reaction was neither.

"This art style is way too old-fashioned Eastern. You'd need quite a lot of imagination to get excited by this."

Well, of course it was old-fashioned Eastern since this was, in fact, the ancient East.

"What does Sworn Sister think?"

"How can you insert it while holding both knees? The thing would have to be over a foot long… Besides, your knees would be shattered like that. Unusable."

"Hmm, customers, don't you feel anything, yong?"

"Not particularly?"

The Divine Thief drooped his shoulders in disappointment.

Then he mumbled something under his breath, which Qing, wary of the unidentified Unrestrained Realm Master, understood.

-Strange. I thought she recognized it. Maybe not. Fuck me, I'll die of old age before finding a successor

Qing immediately thought:

\textit{Ah. I shouldn't stay here any longer.}

Qing fiddled with the books to pass time.

While it wasn't good to stay here, she thriftily checked if there might be other martial arts manuals.

Unfortunately, there didn't seem to be any more proper secret manuals.

Meanwhile, whether due to Qing's advertising effect or not, the merchant forcibly sold a few more books, earning gold sycees for nothing.

Seeing that, being a successor didn't seem so bad.

\textit{If it weren't for my master, would I have become a successor?}

\textit{But what does being a successor mean?}

\textit{Successor to an unscrupulous merchant?}

\textit{Judging by the Righteous Karma, he doesn't seem like a bad person, but due to the forced sales, the number has decreased by two since I first saw it.}

"It's been one ke, right? Can I go now?"

"Want to stay one more ke, yong? I'll give you double, yong."

"That's still just four coins…"

"Then ten times?"

"That's only twenty, hmm. Twenty for one ke isn't bad, but I have some business to attend to. If I have time after, I might drop by again."

"Alright, yong. Thanks to you, I sold quite a bit, yong. Here. I'm in a good mood, yong. It's a bonus, yong."

The Divine Thief flicked a coin.

"Come on, I wouldn't even give a beggar just one coin. If you're going to spend, spend big. You're just wasting precious coins and getting cursed at."

"If you know coins are precious, you'll soon be rich, yong. Take care, yong!"

The Divine Thief pretended to wave goodbye.

Only after the three disappeared into the crowd did he mutter quietly.

"A Peerless Beauty Under Heaven with the Fushen-di. Was that her servant behind her?"

The coin the Divine Thief gave had a special tracking scent on it, allowing him to track from afar once someone had held it.

In the black market where prices were inflated and everything was expensive, there was no need to use coins, so if they didn't throw it away, it wouldn't flow to others.

From their conversation, she didn't seem like someone who would throw away coins.

"But the Fushen-di, is it. It's a treasure no Divine Thief in history has ever possessed."

The Divine Thief grinned.

And yet, he didn't even realize his own martial art had been stolen.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Although they were supposed to meet at the ya shang gathering, the other two in the group seemed to be lost in sightseeing.

In fact, Qing had only been held up for one ke by the strange merchant selling martial arts manuals.

The two were probably still in the middle of looking at and selecting poisons/antiques.

Thinking she should take care of business first without waiting, she wandered around, and finally, Namen earned his keep for the meal he was given.

"It's that person. The ya shang who bought the old man's grandson is right there."

Qing smacked the back of Namen's head.

"You should at least speak properly, you know? He wasn't the one to buy, rather you sold, right? It's not like you were sitting there saying ‘For sale', was it?"

"Th-that's right…"

Qing approached the ya shang Namen pointed out.

He was a vicious-looking man with burn scars covering half his face.

Before she left for Jianghu, Qing might have been intimidated just by looking at someone's face, but now she was too much of a Master for that.

The other person would have to at least be in the Unrestrained Realm for her to lower her head, hunch her shoulders, and carefully gauge the situation.

As it happened, he was the most evil bastard with Evil Karma about one and a half times higher than other human traffickers.

It was incomprehensible why this stupid unorthodox faction bastard sold the child to such a person.

"Hey, you there, Big Scar. Human trafficker."

"Are you calling me? Girls these days have no fear, huh? Hmm, why? Did you come to sell yourself? If you're selling, I could give you gold sycees in the form of gwan, treating you as top quality."

"Then it should be about fifty thousand gwan. Forget it. I came to get back a young man you bought."

She had thought it was some kid since they called him Old Man Ban's grandson, but he was apparently a sturdy young man of nineteen this year.

He's not an adult yet, so you could still call him a child.

For commoners, nineteen would be young for an old man's grandson, even though Wulin practitioners marry much later.

If his head was all white, he would be waiting for great-grandchildren or watching their antics by now.

At any rate, Big Scar smiled slyly at Qing's words.

"Well, if you have enough money, there's no problem."

"His name is Ban Jagwon, the metal shop's grandson. He's a bit shorter than me, has thick eyebrows, and a dark complexion with lots of moles, or so they say."

"Why don't our little pussy cat start by telling me when he was sold?"

It was childishly immature to emphasize that word like that, as if he were some ten-year-old kid.

"Shut up, when was it?"

"It should be about ten days ago."

"What, ten days? I'm speechless, really. Do you think we're some poverty relief organization, keeping goods for ten days, feeding and housing them?"

Qing frowned.

Damn, it's not going to be easy after all.

"You've already sold him?"

"If it's the metal shop son, I do remember. He fetched a good price since he knew some metalworking."

"Who did you sell him to?"

At this, Big Scar wagged his finger.

"I have to protect client information. With the law prohibiting slavery, how could I do business in this field if I revealed who bought them?"

"Hmm. How much would it take? Ten gold sycees?"

It was a negotiation tactic of sorts.

Thinking if she offered ten, he might counter with about twenty.

Gramps had given her plenty of gold sycees, so if not for this, what else would she use them for?

However, Qing's plan immediately fell apart.

"Didn't you hear me? I told you I'd be finished in this business if I sold out clients. Is there an idiot who'd throw away their life for such petty cash?"

"Petty cash? It's ten gold sycees."

"Even if it were ten gwan of gold, not just sycees, it wouldn't be enough. I told you, my life would be forfeit. We have our own rules too."

"Rules? For vermin who sell people? Even a passing dog would die laughing."

"You bitch, your way of speaking is really like a dog-"

"Enough. The price of a life, you say. Will you tell me if I pay the price of a life?"

At this, Big Scar's eyes changed.

"The price of a life, hehe, now I see you're quite the noble. I've been in this business for a while, so you'll have to pay quite handsomely."

"Oh? How much?"

Big Scar should have looked carefully at Qing's expression.

Her pupils contracted, and a faint purple sinister energy rose from their center, looking extremely vicious.

Along with her mouth split wide open to her ears, it was an utterly ferocious expression.

"First, enough for me to get away- Ack!!"

Big Scar, who had been speaking obsequiously, suddenly screamed.

When you're kicked between the legs and float about a zhang in the air, anyone would stop mid-sentence and scream.

This was the lineage-ending strike of the Absolute Witch that all the soldiers of Sichuan feared, and even those who had witnessed it directly still couldn't sleep at night due to the psychological trauma.

Big Scar, who had risen vertically, fell vertically according to basic scientific facts.

Qing grabbed Big Scar's ankle as he fell and crushed it in her grip.

"Argh!!!"

"You're overreacting. Just because your balls burst and your ankle got crushed, you scream like that? Are you even a man? Just cut off your dick, why don't you. Hm? Wait. Maybe you are not a man anymore?"

"Keurk, keueurk."

"Not coming to your senses? I was going to leave you one side, but I guess not. It's much better to hop on one leg than to be completely crippled, right?"

Qing said as she kicked Big Scar's back repeatedly while he clutched his groin and curled up.

However, he was in such pain that he couldn't even properly feel the crushed ankle, so how could he come to his senses after just a few dozen kicks?

That's when it happened.

With a loud patter of footsteps and rustling of clothes, martial artists dressed in custom-made black clothes surrounded Qing.

"What is this! How dare you cause trouble in the black market!"

"Dare? Are you serving the Emperor or something? What's with the ‘dare' from mere night market organizers?"

Their martial prowess was mediocre, with a few First-Rate and two Peak Realm mixed in, so there was nothing to be afraid of.

"You say you'll put up a hefty bounty? Go ahead. My name is Yun Yuanling of the Jin Prefecture's Un Clan. Also, this girl has nothing to do with this."

"Huh? Sworn Sister, but-"

"It's okay. I have a plan. Anyway, they just watched, so they're not involved, right? Now, Sunling, step aside for a moment. Give me the flute. Namen, you've finished your business too, so you're free. Go."

Jian Buxi hesitated but eventually drooped her shoulders and walked away.

Surprisingly, the black market warriors stepped aside willingly, either because they were reluctant to put up multiple bounties or because they were following rules.

If they hadn't let her go, Sworn Sister was about to become Ximen Qing, disciple of the Zenith Among Women, but it seems that wasn't necessary.

"Alright. Now that business is done, get lost. I have something to discuss with this guy. Hm. Hey. Are you not coming to your senses yet?"

"Kheuk, you crazy, crazy bitch. To pick a fight with the Black Store…"

"Right, this Yun Yuanling is a crazy person. So if you had spilled everything for ten gold sycees, you wouldn't have become a eunuch. I really don't understand. Receiving ten gold sycees vs. becoming a eunuch. And you choose the latter."

"You bitch, you are now a dead person wal- Argh!!"

Qing stomped on Big Scar's hand.

With the subtlety of the Heavenly Demon Reigning Step applied, the sensation of the joints under her foot crumbling like sand was indescribably ecstatic.

At this, a black market warrior shouted angrily.

"St-Stop! What are you doing!"

"I don't want to. Aren't you going to put up a bounty anyway? So why should I stop here? Will you cancel the bounty if this Yun Yuanling stops here?"

"You really look down on the Black Store, don't you!"

"Yes, yes. This Yun Yuanling really looks down on the Black Store. Why should the great Yun Yuanling of the Jin Prefecture's Un Clan be afraid of an organization that just gathers all sorts of dog-like bastards and dregs that need to turn into crotch beggars to run a night market?"

"How dare you!!!"

"If you're pissed, come at me."

At this, the black market warriors hesitated.

She was so blatantly picking a fight that it actually made them afraid to charge in.

"If not, just watch."

Qing waved her hand dismissively and then firmly stepped on the back of Big Scar, who was trying to slyly crawl away.

"So, where did you sell that young man?"

"I'll talk! I'll talk, so please spare my life…"

Only then did Qing smile and say:

"That's why I told you. That I'd pay the price of a life."