\chapter{Black Market Commotion (1)}

The black market is a kind of flea market for everything.

More precisely, it was a night market that removed restrictions on items and excluded business ethics from a flea market.

They sell anything, but fakes and stolen goods are rampant, and overcharging and swindling are everyday occurrences.

"What? There are such trash like a tourist merchant association? Don't fights break out?"

"If you break the black market's rules, assassins from all over Wulin will come after you. The Black Store Manager puts up a huge bounty."

"Black Store Manager? The black market has a separate owner? Huh? Wait, there's an owner but they leave it in such a mess?"

"It's more profitable that way. That's the kind of place it is."

Usually, people from Zhongyuan only understand what this means after hearing such an explanation and actually visiting.

However, Qing understood immediately upon hearing the explanation.

So it's like that secondhand market website, Joonggonara.

That place where new items, used items, fakes, and stolen goods are rampant, and overcharging and swindling happen daily.
"So, where is it?"

"The location changes every time, but with a few silver pieces, we can find out the place right away."

"Wow, if we didn't have our Zhugie, we might have wandered around for a long time. As they say, having one smart friend is really convenient."

"You speak the truth, Sister."

After praising him, an annoying self-compliment came back.

\textit{Strange. Was he always like this?}

\textit{I thought he was a bit more modest.}

\textit{Is he the type to show his true colors when you get close?}

Qing couldn't have known, but it was actually a perfect answer.

Rather than being a characteristic of Zhuge Lixian, it was the temperament inherited by generations of the Zhuge family.

Even that great ancestor Zhuge Liang became more and more of an unpleasant, boastful bastard as an individual the closer you got to him.

And in fact, because he was actually that great, he was doubly unpleasant.

Thanks to this, just as Qing was at a loss for words, Jian Buxi returned with a bright smile.

"Sworn Sister, I'm back!"

"Huh? Oh. Why are you so hyper?"

Her excitement had increased noticeably, so it seemed she had risen in realm after eating those Elixirs.

"Yeah, yeah! I'm a Peak Realm martial artist now too!"

"You've gained enlightenment, I see."

"Enlightenment? Is that so?"

Jian Buxi tilted her head.

At that, Zhuge Lixian politely added.

"Originally, enlightenment is not a concept clear enough to put into words, so you might not understand well. Congratulations on your Grand Star."

"Yes! Thank you!"

It was just that Jian Buxi was stupid, but she actually had good intuition, so she understood well why Qing had expressly asked for cleanup.

She had also learned from Sister Xue's Zhongyuan common sense lectures that the Bliss Palace's training methods were greatly looked down upon in Jianghu.

At this, Qing looked at Tang Lan-Ah and spoke.

"Tang Lan-Ah should work harder."

"What? I have poison, you know? With that added, I'm stronger than her, right?"

Tang Lan-Ah wagged her finger at Zhuge Lixian.

Tang Lan-Ah was only a docile quack doctor to Qing; originally, she was a villainess who had put all her points into beauty instead of character, with no trace of manners or consideration for others.

Qing stroked her smooth chin for a moment, pondering deeply.

The Tang Clan's poison, huh.

"Hmm. Acknowledged. With poison added, you could probably be considered as Late Stage Peak to Early Stage Transcendent. Then Zhugie should strive even harder."

"Sister, isn't knowing one's shortcomings a virtue of a noble man? This little brother knows his shortcomings well."

Zhuge Lixian answered with a gentle smile.

Since he was smart, he couldn't even be teased, so Qing just snorted.

After that, they left the Ban Family Metal Shop and followed Zhuge Lixian's lead to a shabby tea house.

Is it really true that good restaurants always look a bit old and rustic?

Qing excitedly ordered a lot of snacks, but they came out quickly, looking very dry as if they had been made long ago.

They didn't taste good either.

Qing took out her anger on the snacks.

Meaning she ate them like a pig.

Meanwhile, Zhuge Lixian got up to find the tea house owner, and she thought he might complain, but he came back asking only about the news that the black market was being held near Suyahu Reservoir in the east, completely omitting the story about the terrible snacks.

"No, with snacks like this, is the black market important right now? I need to see the owner's face too."

"Didn't you already eat them all? And originally, this is just a front business for the Black Store, so you're probably the first customer this year to actually order snacks. But isn't that Longjing tea? Why is there frost on the teacup? Even if it's a front business, serving cold Longjing is going too far. How dare they pull such a terrible trick on guests of the Zhuge Clan…"

Zhuge Lixian showed a genuinely angry expression.

It might be good to let him overturn this terrible tea house, but Qing frankly admitted instead.

"Ah. I put some thin ice in it with my Ice Arts. I like to drink it a bit cool. Want me to cool yours too?"

"My goodness! Sister, are you insane?!"

Thwack!

Qing performed the nuclear noogie she had learned, hitting him on the head.

"Aargh!"

"This is getting more and more out of hand. Zhugie, do you want to see your big bro- no, me go crazy? Want me to show you?"

"No wait, Sister! What kind of peerless Divine Arts is this, ow."

Zhuge Lixian couldn't finish his sentence as he rubbed his head furiously.

Qing snorted.

\textit{For a guy with a mountain-like build, he sure whines a lot.}

\textit{If he got a taste of my master's OG fist, his head would split open.}

"What kind of monstrous strength… monstrous strength…"

Zhuge Lixian, who had been rubbing his head, suddenly put on a serious expression.

"Um, by any chance. When you stayed with the Zhuge Clan, did you visit the Peerless National Scholar Training Ground?"

"Peerless National Scholar?"

Qing's expression whispered to Zhuge Lixian.

\textit{What's that, is it something to eat?}

"Peerless National Scholar refers to…"

It was quite an amazing talent to ramble on for almost half a ke about how it meant the best talent, a scholar without peer in the country, combining the characters for country, scholar, without, and peer.

It was only then that Qing finally understood the meaning of "peerless" that was occasionally used.

\textit{Ah. So that's what it means.}

Having forgotten about the training ground story while explaining, Zhuge Lixian, satisfied with showing off his knowledge, brought up the next topic.

"It would be good to eat a hearty dinner in advance and then set off for Suyahu Reservoir. They do sell food at the black market, but you might end up eating human flesh if you're not careful, so it's better not to put anything in your mouth at all."

The words about eating dinner in advance were welcome.

The words about eating heartily were also welcome.

But it was sad to just look around at a night market without eating anything.

"Then if we eat something other than meat…"

"I won't stop you if you want to eat centipedes, spiders, scorpions, and the like."

"Hmm. I ate too much of that when I was a beggar. It wasn't tasty. No, it's not like I will eat it raw, right? Would it be different if we sprinkle some seasoning and grill it?"

At this, Tang Lan-Ah suddenly interjected.

"What? You were a beggar?"

Qing was at a loss for words for a moment.

"Hmm. Lan-Ah. What do you mean by that? Does the high-born young lady of the Tang Clan not share a table with beggars?"

"No, no, no, that's not what I meant. I was just surprised, and I absolutely didn't say it to make you feel bad. I'm sorry, Qing'er, we're friends, right? Right?"

"Yes. We're friends. You don't have any friends besides me. Be grateful."

"Yes. Thank you…"

It was exactly like how a friendless loser would act, stumbling over their words and clinging on after realizing they had spoken thoughtlessly, so Qing understood and let it go.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After that, they ate dinner and left Zhumadian.

Emblems that could identify affiliations were forbidden, so they couldn't ride the Zhuge Clan's special carriage.

Even without that, they had to walk because if they rode a carriage, they would be robbed or other passengers would take it.

So they walked together, chatting along the way, with no particular scenery to see in the dim early spring night.

"This is unexpected. I didn't know you would offer food to that lowlife too. I thought someone like you, Sister, would put a bowl on the ground and fill it with spoiled rice, telling him to eat like a dog."

Tang Lan-Ah nodded beside him.

Qing spoke, dumbfounded.

"What kind of person do you think I am? And no matter how much you hate someone, you don't mess with their food. Even if it's someone you need to kill right away, you should feed them and then kill them."

At this, the Namen Sect martial artist flinched.

To be precise, no matter how much of a bastard someone is, you shouldn't prevent them from eating.

If you really need to kill them, you should feed them plenty of deadly poison, but it's too much to prevent them from eating at all or just make them watch.

It wasn't some grand belief, just that Qing had experienced a lot of sadness regarding food, so that's how it turned out.

As they chatted like this and crossed a hill, a huge night market spread out on a field behind a large lake.

With over a thousand yellow lanterns visible, the gathering of tents hanging from them was as impressive as a small city.

"Sister, you should take off your face veil now. You cannot cover your face in the black market."

"Huh? Didn't you say emblems that could identify affiliations were forbidden? But now I have to show my face?"

"That, you see, is a story that goes back to the origins of the black market. The past Black Ma…"

To summarize, it was a place where you shouldn't hide your identity too much or reveal it too much.

Even if you meet someone you know there, that's all there is to it, you shouldn't talk about meeting publicly outside.

You should treat it as if you just saw their face in a dream and act like it never happened.

So emblems that reveal identity are forbidden.

Officially, because someone who has never visited the black market shouldn't be walking around with emblems.

But you have to show your face.

This was just a rule the black market unilaterally decided to prevent troublemakers.

"So it's just the tyranny of the sellers."

Anyway, it was welcome news that she didn't have to wear the face veil, so Qing took it off and held it out to the side.

Of course, taking care of it was Jian Buxi's job.

"Hey. Namen. Where do we go now?"

"The, the ya shang are always in the deepest part."

"To prevent the merchandise from escaping, of course."

Zhuge Lixian added a commentary.

That chatterbox really never rests.

\textit{Does he have muscles in his mouth too?}

Slave traders in Zhongyuan were called 'ya shang'.

The fact that they had a separate job title because they found it a hassle to voice out slave traders shows how widespread the slave trade culture was in ancient, primitive China.

It was the same in Qing's homeland.

Human traffickers are the number one most beloved profession among the Chinese people, boasting the second largest scale in the whole world, with a very efficient and scientific system including systematic distribution processes, and disassembly and export according to classification.

Of course, they claim it's punishable by death if caught because the Party's pride is hurt by not being number one in the world.

However, in reality, it was closer to a performance than actual execution, as about six-tenths of the amount earned from selling one person went to the communist aristocracy.

For reference, the homeland of human trafficking, the paradise of human trafficking, the great originating country of human trafficking and the overwhelming number one in rankings is a populous country located across high mountains to the southwest of Zhongyuan.

It was also a country of terrible criminals where the entire population (in this country, women are not considered people so they're not included in the population) were sex offenders and robber-murderers with pickpocketing as a side job.

If you travel alone by any chance, the probability of returning is only fifty-fifty.

For women, it's guaranteed to be a one-way trip, so if you're a man, you might as well start believing in the power of statistics.

Anyway, the group passed through the black market smoothly.

As they walked, a deliciously savory smell wafted up, making their mouths water, and after quite a while, a flag with "Wangfujing" appeared.

An entire alley was filled with grills heating up iron plates to cook, so the smell spread far and wide.

And surprisingly, the source of the delicious smell was skewers of all kinds of grilled insects!