\chapter{Black Market Commotion (4)}

He was already a man who wouldn't live long even if Qing let him go, having become crippled in both legs and hands, and having sold out a customer.

Big Scar knew this fact too, but naturally, the crisis right in front of him was the most important.

That's why Qing deliberately acted even more cruelly.

It was a hint that if he defied her saying he was already a dead man anyway, she would create an even more terrible end for him.

"That young man is-"

"Halt! You bastard, how dare you try to reveal client information when you're registered as a Black Store member. Kuk."

There was someone trying to stop Big Scar's mouth.

Qing, who had confirmed his Evil Karma, threw her hairpin.

A First-Rate black market warrior fell, clutching his neck.

Three Birds One Chopstick is a Third-Rate hidden weapon technique that only throws straight without any other tricks.

But combined with superhuman strength and the Inner Qi contained in the throwing weapon, human bodies have no way to withstand it.

"Is there anyone else who wants to talk? I'm sure you all have eyes, so you can see how many I have left in my hair, right?"

It's not uncommon for women to use iron hairpins as hidden weapons.

However, it was unheard of for a thrown iron hairpin to not just stick in the neck but pierce through it and come out the other side.

Two Peak Realm Masters among the black market warriors exchanged glances, and one of them spoke.

"…Do you have any more business in the black market?"

"No. If he hadn't stopped me, I would have finished my business and left long ago."

Qing pointed at the fallen black market warrior.

Then the black market warrior lowered his voice.

"The Black Store will remember this. A thousand gwan bounty will make assassins from all over the world, no, even those who aren't assassins, go crazy. We'll see how long you can last. Yun Yuanling, was it? The fallen Yun Clan of the Jin Prefecture's lineage will end."

And then saying "Let's go," he left, and the other black market warriors followed with visibly relieved expressions.

They didn't have confidence in winning if they charged in, and she didn't seem like someone who would listen if they tried to stop her.

Even if they won, since the Black Store wasn't a force-based organization, each Master was precious, so it would be a battle with more losses than gains.

So if they weren't going to fight anyway, rather than stupidly just watching the violence, they judged it better to leave a stern warning and depart, creating a more plausible scene.

After that, she heard Ban Jagwon's location and retrieved her hairpin.

Then Jian Buxi came running.

"Sworn Sister, are you okay?"

"Yeah."

"What are you going to do now? If the bounty is a thousand gwan…"

"Well, after killing a few assassins, they'll realize their lives are precious and it'll die down. Just in case, it would be better for Sworn Sister to return to the Xue Family Trading Company."

"Can't I stay with Sworn Sister? I'm a Peak Realm master now too."

"Then what about the old man's grandson? Either of you meet him and tell him that kid was bought by the Dabie Sect on the Dabie Mountains. Tsk, those so-called Orthodox Factions buying slaves. But since they're orthodox, he probably isn't suffering too much."

It seemed they bought him intending to raise him as the sect's blacksmith since he knew how to work with metal.

And now, either the Zhuge Clan or the Tang Clan, or both together, were planning to go, so there shouldn't be any problems after this.

"Then, what about Sworn Sister?"

"I'll just lay low for a couple of months and then go to Kaifeng in time for the Wulin Conference. It would be good to report this incident to Master too. I'll ask you to do that."

"Because I'm weak and can't help…"

Qing grinned.

"This is you helping, you know? What else could be of help? Do you have to stand back to back with me and break through, leaving a trail of blood, to call it help? Without Sworn Sister in the morning, I'd have to dress and wash alone, ah, just thinking about it is annoying."

"Yeah…"

Qing held out her hand without erasing her smile.

Jian Buxi made a tearful face and grasped that hand.

Then Qing spoke.

"No, what? Why are you holding my hand? I'm asking for the face veil. The face veil."

"Ah, right."

Qing, who received the face veil, leapt up swiftly.

She jumped up with the Anti-Gravity Steps of the Divine Maiden Footwork, stepping on the poles that held up the temporary tents of the night market, and flew away with the Thousand Li Flight.

Her speed was so amazing that even a Master of Qinggong would find it difficult to catch up.

It was an escape speed even Ximen Surin acknowledged.

In fact, she said if Qing was determined to run, those who would be able to chase her could be counted on one hand in the world.

However, she said they could be counted on one hand.

She didn't say there were none.

"Why is this damn brat's feet so fast? Let's see, that looks like the Thousand Li Flight. Oh ho, not only are her feet quick, but her Qinggong is already excellent. If she just has good hand skills, she'll be perfect!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The past merchant world was heated with the Black Sky Association's defection.

The Black Sky Association is a notorious human trafficking group.

They were the real deal, with the skill and execution to carry out kidnappings across Zhongyuan, and even connections reaching the Western Regions to bring in precious red-haired slaves.

But suddenly, they spouted nonsense about living righteously from now on and left the industry.

The problem was that they killed all the related workers like brokers, warehouse keepers, teachers, etc., before leaving.

Moreover, they didn't just kill the related workers but massacred their entire families, hanging the corpses in the market and carving "human trafficker" on them.

So no one mourned them, instead spitting and throwing stones, saying they died well.

With such miserable ends, many in the business quit, and no newcomers were entering the industry.

Because of this, the Black Store took a proper hit.

The Black Store isn't just an organization that opens black markets - night markets - and lives off commissions.

If there's a deal in Zhongyuan that can't be spoken of to others, it all happens through the Black Store, so the black market is just a part of the Black Store, and all kinds of black market traders settled in every city were actually affiliated with the Black Store.

So in reality, the slave industry workers who were massacred with their families were all deaths of Black Store members.

The previous Black Store Manager raged furiously, but in the end, couldn't catch the Black Sky Association's tail.

To be precise, they were left with only a strong suspicion, almost a certainty, that it was a front for the Demonic Cult bastards.

However, they couldn't touch the Demonic Cult with mere suspicion.

Amidst the public sentiment that those sons of bitches deserved to die, it was futile to rise up in anger and pour out criticism.

People would just say, "Wow, the Demonic Cult did a good deed for once."

Moreover, if the Demonic Cult touched them, the Black Store would be crushed.

Weren't they the war group that left deep scars on the Orthodox Wulin in the four Great Wars Between Orthodox and Demonic, even though it was just a series of defeats?

A war between such a Demonic Cult and a suspicious, secretive black merchant union couldn't even be established in the first place.

No matter how much overflowing wealth they had, who would respond if they shouted, "We're going to war with the Demonic Cult, who will fight for money!"

In the end, they had no choice but to swallow their anger with nowhere to go.

But then a problem arose.

A slave trader was brutally murdered in plain sight at the Henan Branch of the black market.

To be precise, it wasn't murder, but an incident that left him in a state where death would be preferable.

Zhang Enchai, the Black Store Association Leader, clutched his head.

"Why! Why! Why! Why are they doing this to me!"

"The slave traders' dissatisfaction is no small matter. They're even organizing their own association to protect themselves, so we've caught and killed the instigators for now. But at this rate, it's only a matter of time before the slave traders defect."

"Fuck… We haven't even cleaned up the mess those Black Sky Association bastards made properly."

"We'll put up a bounty for now, but if we don't make an example of what happens to those who touch the Black Store this time-"

"Five hundred gwan."

Zhang Enchai cut off the chief's words.

The chief frowned.

"Pardon? You're saying just five hundred gwan? With that…"

"Yun Yuanling, was it? Say we'll give five hundred gwan for her corpse, ten thousand gwan if brought in alive. We'll deduct two thousand gwan for each limb, so tell them to bring her in one piece if possible."

Zhang Enchai's eyes were chillingly cold.

"This time, we'll clearly show the world what happens when you mess with the Black Store. Human pigs aren't the exclusive property of Empress Lü."

Empress Lü, who proudly made the list of China's Four Great Villainesses, ranked high for her cruel nature and creative torture.

Human pigs were strictly forbidden as something horrific even in the long history of Zhongyuan, so it was a terribly vicious grudge to say he'd capture her alive and make her into that.

Unable to touch the Demonic Cult out of fear and burning with rage inside, now that someone had slapped their face, that anger had no choice but to be directed fully at her.

"It's already time for the Black Store to show some movement to appease the slave traders, isn't it? In a way, this could be seen as a good thing."

Zhang Enchai smiled coldly.

But would things really go as he wished?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Black Store put a bounty on Yun Yuanling.

\begin{quote}
Black Store Special-Grade Wanted: Yun Yuanling.

Five hundred gwan of gold for her head.

Ten thousand gwan if captured alive. Deduct two thousand gwan for each limb.

Characteristic: A beauty recognizable at a glance.
\end{quote}

Many people had seen Qing at the black market.

So when asked what she looked like, they all gave stupid descriptions like she's pretty, very pretty, really pretty.

"No, I'm asking how her eyes, nose, and mouth look!"

"Well. Her eyes are large and clear, beautiful, her nose is straight and flawless, beautiful, and her mouth is small and red-"

"Beautiful, you say?"

"Yes, that's right."

"Ugh. Next!"

But they were all the same.

If asked to describe her eyes, nose, and mouth separately, they'd say pretty, if asked about her characteristics, they'd say pretty, if asked about her impression, they'd say pretty again.

The listeners were all curious about what kind of beauty she could be.

So when the black market mobilized all their painters to draw wanted posters, everyone cried out that the pictures couldn't do her justice.

Even in Qing's homeland, the reliability of facial composites made only from testimony without video was quite low, so how much worse must it be in Zhongyuan?

Finally, when something that looked somewhat similar came out, now began the hellish copying process.

Of course, there was a method called printing.

The Zhongyuan is the birthplace of human printing technology!

Ever since a person named Bi Sheng commercialized clay printing technology for the first time in human history, Zhongyuan has exerted its dignity as the originating country of printing technology.

There's a strong suspicion that they probably made the first metal movable type as well, but due to the double attack of the Cultural Revolution and the Backyard Furnace1, not a single piece of physical evidence remained, so it wasn't recognized.

Thanks to this, the honor of inventing the first metal movable type went to the Korean people.

Surprisingly, both the Cultural Revolution and the Backyard Furnace were achievements of a single human being, and because of this, he was ranked second among the most respected figures by the Chinese people even in modern times.

Since the first place is always occupied by living power and the dead cannot intrude, he was essentially first place.

Anyway, even with such excellent printing technology in Zhongyuan, it was still primitive compared to modern times, so the portrait was too delicate to be produced with woodblock printing.

For now, they were copying and distributing as they were completed, but the number was woefully insufficient.

Moreover, bounty hunters and assassins were tearing off the papers with the portraits drawn on them and hiding them in their bosoms, wanting to eat alone.

So in the end, only the wanted news spread widely.

Very pretty top-class beauty Yun Yuanling of the Jin Prefecture's Un Clan in Zhongyuan (Virginity Unknown).

Ten thousand gwan of gold if captured alive!

And so, the result.

"Oh my. There's a bitter poison scent in the tea? Xinpa, do you have some grudge against me?"

Yun Yuanling said, sipping her tea.

The old woman who was about to place her next move on the Go board withdrew her delicate hand with a start.

"…What did you say?"

Yun Yuanling rolled the tea in her mouth, tasting it, then swallowed with a gulp.

"Mmmmmmm. This taste is Dream Soul Incense. My goodness, am I some kind of daxiang? This isn't an amount you can sleep soundly for fifty years, is it?"

In Zhongyuan language, elephants were called "daxiang."

Xinpa, a Great Demonic Adept even among the Demonic Adepts, who in turn were among the Demonic Adepts that Jianghu people called the White Hand Demonic Sect, became enraged.

"How dare some bitch…!"

And so, she gathered all the household members of the estate to have a time of contemplating the truth together.

Since water and fire always know the answer, it wasn't long before the culprit confessed their sin.

"I, I have committed a mortal sin. I was blinded by money and…"

"Money, you say. Did someone hire for an assassination?"

"The Black Store put out a wanted notice, and the amount is as much as ten thousand gwan…"

At this, Xinpa turned to look at Yun Yuanling.

"You bitch, what trick did you pull on the Black Store?"

"You know, even if you say what trick I have pulled… I've done so many things, I'm not sure. Perhaps I underestimated the Black Store too much. Those insignificant creatures somehow managed to identify me. Excuse me, would-be assassin? Are you certain it was me?"

"It's Yun Yuanling of the Jin Prefecture's Un Clan, and the characteristic is a beauty recognizable at a glance…"

At this, Xinpa snorted.

"Hmph. It's certain alright. They say if the tail is long, it gets caught, don't they? I told you so many times to wear a human skin mask at least."

"Oh my. I'm already wearing a human disguise, what difference would one more layer make? I guess I underestimated the Black Store's pitiful intelligence too much."

"Then, what shall we do?"

"I only let you live because it was convenient for getting materials, but it's bothersome to leave a fly buzzing around without knowing its place. Oh my, this is troublesome indeed."

Yun Yuanling continued with her characteristic gentle and elegant smile.

"For now, as a warning, let's clean up everything in sight. Will you help too, Xinpa? You should enjoy your hobby once in a while, shouldn't you?"
