\chapter{Heaven and Earth Simp (1)}

By the time we arrived in Xi'an, it was not difficult to find bright signs of spring here and there.

On the ground, green was slowly sprouting among the dull, yellow, dead grasses that have been there all winter.

"Now, look. This is it. This is it. This is it. What is it?"

Qing approached the zelkova tree leaning against the wall and spoke, and Ciyu, who was hugging it, looked at the light green buds hanging from the branches as if she was amazed.

After all, to those from Qinghae, the plants and trees of Zhongyuan were the most amazing and strange things.

Even though he had never really experienced the land of Qinghae before, being confined there, he seemed to be quite concerned about the abundance of trees.

"What is it? A sprout? No, the sprout seemed a little different."

It was a sudden thought that I couldn't think of, perhaps because I didn't have much to write about.

"It's a flower bud, a new bud."

"Ah. That's right. New sprouts. Anyway, it's growing here. Grass grows, flowers grow, and fruit, that is, fruit grows."

"fruit."

Ciyu swallowed hard, then stretched out her hand towards the new shoot and ripped it off.

And then pop it into my mouth. Yum yum yum.

"Ugh."

Of course it doesn't taste good.

It was a woman who stuck out her tongue and licked off the half-crushed shoots of the Chinese juniper tree.

And then he looks at Qing with a look that's somehow rebuking. What was it? Why was he looking at me after eating it himself? What does it mean?

"fruit."

So, what I'm saying is, even though it's called a fruit, it doesn't taste like fruit, but rather tastes bitter, sour, and sour, and even though it's good for your appetite, it's so delicious that even a person who eats inedible things as their staple food can't eat it and would spit it out.

He chuckles and laughs.

"You said it grows into fruit, not just fruit? If it were delicious, I would've picked it and eaten it first. It's not that easy, you know. If something's good, someone's bound to snatch it first. So, there's no need to put something so common in your mouth—"

"Tsk. That's a great lesson for the kid. Good job."

"What? Life was a battlefield, isn't it? You have to experience bitterness to come to your senses, and even the snobbery of putting anything in your mouth can be corrected."

Paengdaesan naturally ignores Qing's protest as if he had not heard it at all and hands Ciyu a candy.

It was the so-called educational candy.

I wonder if a curriculum that rewards students for memorizing letters was really right.

"Now, be careful, if you pick up anything and eat it, you could get really sick."

Ciyu quickly takes the candy and puts it in her mouth.

It's an unbearably cute sight, with a small head and small cheeks that were bulging out like candy.

The group was walking along Jang'an Street (Jang'an Street), which was the center of Zhongyuan trade, west of Xi'an.

Since Qing Dynasty's rebellion in Chang'an, the people of Xi'an have developed peculiar habits.

It was not a Shinto-Bulli, but a Shinsi-Bulli, a primitive, ancient, uncivilized nationalistic ideology that said, "If you're from Xi'an, use Taiqing Shangbang products."

Of course, this was what happens when money from a clear source springs up and the goal was not to make money, but to dominate the market and win over public sentiment.

So, Xi'an and Chang'an have already fallen into the hands of the Taiqing Shangfang.

After acquiring such a dominant position in the market, TaeQingsangbang revealed its vicious, sinister, evil, and cunning nature.

The wicked tricks of the cultists!

Wouldn't they drive out the good moneylenders by lending them money at almost free interest rates?

They commit the terrible atrocity of distributing free meals to the poor and crushing their will to work and desire to succeed.

They tore down old, shabby houses and forcibly built three-story extensions, causing the landlords the pain of managing a large house, while also inflicting the humiliation of having to accept homeless vagrants as tenants.

On the other hand, by giving money to the doctor in advance and having him provide the medical treatment for free, he caused the people of Xi'an to forget the value of medical treatment.

As merchants, they try to look after the interests of others more than their own, so I can say that they were ignorant people who do not know the principles of business ethics.

Now that it has spread its hand across the entire Shaanxi region, it was not difficult to hear the horrific words, "Please, if you were from Shaanxi, use Taiqing Shangbang products."

So, TaeQingsangbang!

In fact, it was an exact repetition of what had happened at the Lanzhou branch of the Xuega Sanghoe.

A slap, a slap, a slap. And another slap.

However, he had already experienced Qing, and there were many faces that were familiar to him, but not unfamiliar.

So the only difference was that the TaeQing Sangbang employees were a little more relaxed about their actions.

After spending a day with such warm hospitality, it was time to say goodbye.

"Hmm. Have a nice day. And give my regards to Choryeo. Oh, now that I think about it, I keep saying I'm going to go out and play, but I keep breaking promises."

If you take the Grand Canal from Xi'an to Kaifeng and from there, you just follow the Grand Canal and flow, isn't that the land of Hebei?

There was no reason to go around Pengdaesan and take the Yangtze River since there was a return route that could be reached by just taking a breath if you took a boat.

Since I was going to my house in Qingdo anyway, I couldn't even come to the Divine Maiden Sect gate as a guest, as it was in Geumnam's area.

"Where were you going? Aren't you going together?"

"I should go home too, shouldn't I? Your mom, or rather, your dad—"

At this point, Paengdaesan's expression became quite bizarre, but anyway.

"-Listen carefully."

"Can't we go together?"

It seemed like he had developed a certain affection for her as a teacher of writing, but Ciyu looked very disappointed.

"Just see me again. Why do you want to stick together forever? I told you to go to the mountain, so even if you go to sleep, wave your hand."

Breakups have always been a simple affair.

If you see it again, it's over.

So, Peng Daesan, boarding.

And Qing looked at Xue-i-ri.

"Why are you standing there seeing him off?"

If we really have to be specific, isn't Gunyeong's house a guest house of the Wulin Alliance?

If the guest house isn't your home, then you don't have a home. And if it's a place with an unlimited contract renewal that doesn't even require rent but even provides an allowance, then it's not like it can be called a home.

"I'm going to buy a house in Zigui."

"Hmm? Do you have money to buy a house?"

"No, but Uncle Xue has."

It was a very confident answer.

She knew that Xue Ga-nom had true wealth, and it was also a blatant declaration of wanting to leech to him and buy a house in Zigui.

"Really? Then what?"

Of course, that doesn't mean that Qing was rude or anything.

Basically, it's the Xue family's family history, so it's not like I'm being assertive or anything like that, or that I left the house to Xue in the past.

If it's going to happen, Qing would be more than happy to move in next door.

When you think about it that way, it really seems like a moral decision.

First of all, Gunyeong. Gunyeong can also stop being the Wulin Alliance's handmaiden, or rather, his handmaiden, so it's beneficial.

I like seeing Gunyeong often.

I told Ciyu that she was still his mother, but I wonder if it would be good for him to see her often, considering his emotions. I'll have to think about it a bit, though, as to whether Gunyeong was harmless to his education or a harmful freeloader.

It was a decision that was even advantageous to the martial arts alliance, which could take back one guest house without giving any allowance.

If just one person, Xuega, were to sacrifice themselves, so many people would be happy, so I wonder if it's only natural that they should give up their homes.

So we took a carriage and headed south.

The western regions of Shaanxi and Hubei provinces were mountainous and rugged, making it quite an inconvenient travel route by horse-drawn carriage.

It wasn't necessarily the case with the state-of-the-art comfortable carriage provided by TaeQing Sangbang.

The only downside to the comfort carriage was that it was hot in the summer because it only had air conditioning, but now that it was still chilly in early spring, it was not a problem because it provided heat with the insulation function and a hidden stove.

So the days kept passing by.

Since Mt. Mudang was located to the north of Mt. Sinnyeobong, its rugged mountain scenery always catches the eye on the way back from somewhere.

But since MucheonmuQingdaeje stopped by at the end, what happened?

Unfortunately, the non-partisan faction will wait until next time.

And as you continue south, you finally come into view of a large stream peeking out between two steep mountains.

The martial arts of the general, and the great city that stretches from the mouth of it-

"Hmm. Every time I look, the city seems to get bigger."

Jagwihyeon was developing at the speed of light, and since winter in the central plains was the off-season for farming and civil engineering, its expansion was bound to be even more noticeable.

Also, it's different from when I saw it last fall, so, um, was this what you call a standout?

Originally, Jaguihyeon was a small city located only on the southern bank of the Yangtze River, an ambiguous existence that was neither more nor less than a small village.

Now, even across the river, the sound of hammers striking trees was incessant, with countless sites already established around the ferry.

"Oh, Miss! You're back!"

"Oh, little lady, little lady!"

"I, I'm really weak, but…"

Occasionally, employees of Xuega Sanghoe would recognize Qing and greet him warmly.

It's true that the employees of Xuega Sanghoe headquarters were less picky, perhaps because they see each other so often.

However, as if it were some kind of national law, they always hand out snack bags, but since there was no notice that Qing was coming in advance, it was really weak and it was funny.

So the three of us, Na-ran and Ciyu, chewed on the jerky and drank only the salty water while crossing the Yangtze River, and passed through the open gate of Xuega Sanghoe, which now felt like home.

"Oh, Mother? You've arrived?"

-A one-eyed young man suddenly pops out.

It was the Alleged Supreme, Yan Hui-yeong.

"Ugh."

Qing's expression suddenly distorted.

"What is it? Why are you here?"

"Hmm. Mother, your reaction is a bit disappointing. But didn't my aunt said anything?"

Qing's head suddenly turned towards her.

It's as if a fierce gaze was directed at Jian Buxi, demanding the truth.

"Huh? Didn't you hear that my nephew was heading to the Holy Land?"

"No, why is this a holy place?"

"Ung, I don't know. It's just like that."

She just thought it was a holy place because it was a holy place.

It was a truly eloquent answer.

"The greatest master in this neighborhood was away, so I came here out of concern that something unpleasant might happen. Shouldn't you be praising me?"

The Divine Maiden Sect Gate was located in the western part of Hubei Province, south of the Yangtze River.

In fact, if we look at it from the perspective of the political situation, it can be said to be a border area with Sapa, so it was said that he came to fill the void left by Ximen Surin's absence.

Of course, Yan Huiyong was also a Profound Realm master.

"Hmm. That's…Thank you. You're being considerate."

A smile appeared on Yeom Hui-yeong's face.

"As expected, Mother, you're always honest about these things. But who is this person claiming your embrace so completely? Isn't she a bit presomptuous?"

Ciyu was glaring at Yeom Hui-yeong.

Qing, come to think of it, oh my.

\textit{Come to think of it, I also have an adopted son.}

Qing cautiously brings up the subject, unsure of how this crazy guy will react.

"Hmm. My daughter? I just brought her here—"

"Oh! What's that, a little sister? I thought she looked so bright and intelligent, but she really is different. She is."

By the way, Ciyu's eyes were not bright at all.

If I had to pick the most similar thing, I would say it's the dull, rotten eyes that were like a dead fish.

"Who?"

"Hmm. I guess there's nothing I can do about it. He's your brother."

"Is that right? Are you brother?"

"Ugh. My heart, my goodness, this tiny thing."

Yeom Hui-yeong falls down, clutching his heart.

Qing looked down at the sight with cold eyes and thought.

The crazy guy was sitting there shaking his head.

And there was a woman who watches that scene and causes a strong earthquake in her eyes.

Of course, there was no way that Qing, who was disgusted by the mere thought of being adopted, would say anything to his friends.

"Young Lady Ximen. This person is…"

"Hmm. It's a bit complicated. Because he's a poor guy, I guess I ended up taking on a role similar to a mother, a father, or something like that. So, it's a similar thing to helping the poor or the needy."

"Yes, I understand."

Xue-i-ri answered.

However, Qing thinks that even she didn't understand, so what on earth did Iri understand?

And then, Xue-i-ri looked down at Alleged Supreme, who was still complaining of heart pain and was also a heart patient, and spoke solemnly.

"Nice to meet you, son."