\chapter{Heaven and Earth Simp (2)}

It was understandable how the word son came about.

Xue-i-ri was Ciyu's mother.

And at this place, she met Qing's hidden(?) son, and that son became Ciyu's older brother.

So, what do you call your daughter's brother?

The answer is, son.

Although, I think it might not have been too difficult a problem for Gunyeong.

But having an eight-year-old kid as your child was a completely different feeling than having a grown, dark-skinned man as your child.

Even if you just look at him, he's older than me!

That's why Xue-i-ri's voice was so tragic.

However, I don't necessarily ask about the situation, and the determination to not ask or investigate was a bit peculiar.

At that, Yeom Hui-yeong's expression suddenly turned sour.

As if he heard something he shouldn't have heard.

Qing felt both exhilaration and empathy.

How about it, you must know how it feels since you've experienced it too, but half of it was like, well, it makes sense if Gunyeong steps forward as the mother's advocate.

"What? Crazy—no, no. Are you a friend of your mother's? Or was she a woman with a slight headache?"

"Oh, it's useless. It's a bit dull, but it's not so bad that it's uncomfortable."

"no,"

"See, it's not like this either."

"Not that. It's not that I'm stupid."

"Oh my, you're so useless. How can you lie without changing your expression even once?"

Anyway, Qing felt the need to sort out the situation.

Looking at the way her son Hosooin was acting, it would be good to have Xue-i-ri take on the role of mother.

What good could come from continuing to offend a dog master (both a complete master and a dog-like master) who was mentally unstable and has a bad temper?

You have to touch someone who can handle the aftereffects.

Bowing down to the strong was never shameful, and rather, isn't it a natural law of nature?

"Um, this is Ciyu's mother, Xue-i-ri. You know Snow Flower, right? Snow Flower of Wulin's Five Flower. And this was Yeom Hwi-yeong, um, my son. Tsk, that's how it ended up."

The expression on Qing's face was blatantly rotten.

But Yeom Hui-yeong was smiling brightly.

"And Ciyu was my daughter, and I'm Ciyu's father. This was Ciyu's mother. This was my son. And to this guy, I'm Ciyu's mother. So, this guy was Ciyu's mother, and I'm Ciyu's father. I may or may not be this guy's mother, but I have nothing to do with this guy…"

A fine wrinkle appears between Xue-i-ri's eyebrows.

It's like asking what were you talking about.

Well, if you continue the family appeals around Qing, it will be a great family tree, and the world will be in chaos.

Well, anyway.

It seems like she understood that she didn't need to play the role of a mother.

"Hmm? So what happens then? Does this little brat become my half-brother?"

"No, who else could possibly be my full brother?"

For half-brothers and full-brothers, the character for belly was used.

This was a term that refers to brothers born from different ships and brothers born from the same ship, and was rarely used in Qing homeland, but it was very common in Zhongyuan.

In the first place, it was a world where it was very natural for there to be multiple mothers, so I thought that would be a waste.

"Well, why were you saying such sad things?"

"Is that okay? Anyway, Grandpa, Grandpa!"

The saying that what you say will come out of your mouth has been around in all cultures.

That means it was a very common phenomenon.

Or maybe it's because he waits for someone to appear and then only appears when someone asks for him, saying, "Now was the moment."

"If you're here, come quickly. Ahem, what kind of punk were you hanging out with?"

It seemed that Yeom Hui-yeong was not a good fit for Choi Ri-ong.

After all, it was Choi Ri-ong, the father of Qing, who was the one who filed the complaint.

It was only natural that the sight of a grown man calling his daughter, "Mother, Mother," would be like a thorn in her throat.

"But what about that kid?"

"Oh, she's Ciyu, Ximen Ciyu. This time, I decided to take her as my daughter."

"Hmm? Why does a woman who isn't even married keep picking up things? Well, she's pretty, after all."

"No, Grandpa, you too. If you're going to say something harsh, you should at least shut your mouth."

Choi Riong's expression was brighter than his words.

"Hey, why are you holding to your Mom so tightly? You're a grown girl, yet you're acting like a baby. It's useless. Can't you come over here?"

Even so, there was a difference in the extent to which the target of the clinging changed from Qing to Choi Riong.

Ciyu couldn't understand at all what exactly was wrong with it.

And then it was time for the usual sumptuous banquet.

As soon as Qing entered the Yangtze River, news of the arrival of the Xuega Sanghoe was immediately delivered, so there was no particular waiting time and freshly prepared, boiling dishes poured out.

Choi Ryong's face had now become noticeably more chubby, and he now looked like any other grandfather.

So, what I'm saying was that after having a grandchild, I started acting like my children didn't matter to me.

"Oh, pork ribs? Are these good? Oh, yes, you really eat well."

Ciyu was eating with her mouth wide open like a hungry baby bird in Choi Riong's arms, yum yum, it was like she was controlling the old man with her fingers.

Well, you know, it's convenient.

On one side, Xue-i-ri was groaning while the hot egg porridge cools on her tongue.

"My younger sister hasn't learned martial arts yet?"

"I'm still debating. I should at least teach a cultivation method, but if I force it, it'll just make her losing interest. What even should I teach? I know so many cultivation method."

"How about the Honcheon-gong? It costs a lot of elixir, but there's no need to worry about that. One person should be able to do it in no time."

Qing sneakily searches for the Honcheon-gong.

Honcheonmagong, gold frame.

But it's Demonic Art.

There was absolutely no reason to risk magic and teach the child something as simple as gold, let alone purple, so it was rejected.

Still, since it was a kind word, Qing uses a nice word to refuse.

"I have the Xu Zhang Heart Cleanse Mirror, the Dragon Elepahant Prajna Cultivation, and the Mansangyeoililgisimwongong."

Up to this point, these were martial arts that could be confidently known and taught to Ciyu.

Qing's voice slightly improved.

"Or is it betterto teach the Yijin Cleansing Method?"

Yeom Hui-yeong also looks dumbfounded.

"No, what the hell were you doing? Where in the world have you been wandering, gathering Divine Arts? Well, if it's a orthodox Confucian, Buddhist, or Taoist Divine Arts, then why the worry? But if there's Yijin Cleansing Method, what's to think about? Just learn it first and switch later."

"Isn't it a bit difficult for a child to get used to it?"

There was a major problem with the Yijin Cleansing Method, which was that it was completely different from other internal energy methods that involved simply reciting sutras and breathing.

Perhaps because it was an old martial art, it was a reverse-modern martial art that used a primitive and uncivilized training method called Donggong.

The pupils must constantly move their bodies while breathing properly, so where does the effect of cultivating the body's bones and blood vessels in the most ideal way come from?

The Yijin Cleansing Method was also the starting point of the martial arts of Zhongyuan, and it was said that Shaolin martial arts originated from here.

In other words, most of the ignorant external training methods practiced by the Shaolin monks were methods derived from the Reverse Realm Sutra.

Starting with the horse, lifting heavy objects, twisting ropes, standing on tiptoes in narrow places, climbing up and down rough mountain paths, and even getting splashed by waterfalls, when you see the training, you can't help but think that this was truly healthy.

Perhaps the ability to control the bones and blood vessels was cultivated through intense physical training of the pupil rather than through the internal energy method.

So if you tell her to do this, she'll do it anyway since she's a very observant child.

I was afraid that my luck that had come to me one day would disappear because my mother suddenly hated me, was disappointed in me, etc.

But it was a very difficult training method.

After all that effort to build up your body to a certain level, you learn a different method in the middle of it?

We decided to start from the beginning? But this time, we just have to sit quietly and breathe, right?

"Is that what you're worried about?"

Yeom Hui-yeong had a look of disbelief on his face.

Well, that was a ridiculous thing to say.

What was the state of speaking about the origin of the world's greatest martial arts and martial arts that cannot be learned because it does not exist and cannot be taught because it was not known?

What if it's too rough and difficult for the child to master and the child loses motivation?

"Shouldn't we at least teach them a lesson, even if it means beating them up? They'll thank us later anyway."

"That's not the problem. I'm just worried the child might get twisted."

"No, Mother? Isn't that how you taught such harsh lessons to someone?"

Yeom Hui-yeong continued speaking, tapping his blindfold.

Qing thought to herself, 'If only I had just blown both sides back then, we wouldn't have to see this'.

\textit{In a way, it was thanks to only one side being blown up that a Profound Realm came to stood guard when Master's seat was vacated.}

\textit{They say you don't know anything about the working of fate. Really.}

"What is this? Are you discriminating against sons? Even if that's the custom of Zhongyuan, this feels a bit excessive."

"No, that's not it. Um,"

Qing delivered a loud, characteristically powerful sound.

The child was not just any child, but a created being, a child who has seen and experienced so much hardship that if she gets upset, it won't just end at the level of throwing tantrum.

If it's just to the extent of being a bad girl, then it's only to that extent and can be corrected with a noogie.

If that's not enough, there's also the last resort of dropping the thermonuclear noogie, the final lesson of the Ximen Surin's education style.

But didn't the three leaders of the Jeongpa Martial Arts Association already know the child's identity and support the adoption declaration?

This was similar to the meaning that the moment a child causes trouble and becomes a source of trouble for the martial arts world, the three of them will come out and take responsibility.

Yeom Hui-yeong chuckled at that.

"Then I have no choice but to pay attention. As her older brother, I can't help but understand that much. Hmm. Usually, things like that can be resolved by training together."

If I'm the only one having a hard time, I feel like I'm the only one having a hard time and feel wronged, but if everyone else was having a hard time, I think it's just how people are.

Of course, you cannot teach the reverse karma to others.

So, it was just meant to save the victims who would suffer together in order to share in their suffering.

Isn't this the kind of thinking befitting the former leader of the Madou group?

"Oh. How could you have such a wicked thought?"

"Why can't you do it?"

"No, that's a good idea, let's do it right now."

What if I don't teach you the process of breathing and accumulating energy, the essence of the reverse karma?

The practice itself was a very healthy way of training the sinews and bones, drawing out the potential within the body, and internally expanding the energy channels and removing impurities from the meridians.

So, I think it would be good to find some training assistants who will share the joys and sorrows with you, or rather, who will only be miserable, and who will practice together with you through thick and thin.

Where did you get these?

Of course, it was a very good training method for the body, so it would be good if the three great disciples of the Divine Maiden Sect gathered together and did some good things for everyone.

It was the moment when Qing's worries entered a new phase.