\chapter{Heaven and Earth Simp (3)}

There was news that was currently heating up Zhongyuan martial arts world.

He was the talk of the town in the martial arts world, and everyone talks about him whenever they meet.

The opening of the Yizheng Martial Study Academy\footnote{義正武學館; Yizheng Wuxue Guan; Righteous Upright Martial Study School}!

It was said that the name of the Yizheng Martial Study School was given by a Wulin leader of the distant past with the meaning of establishing righteousness and justice in the world.

At the time, there were quite a few opinions that said, "Why not just call it Zhengyi\footnote{正義; justice} Martial Study Academy?"

But even without that, the sound that the adults in the Orthodox faction made when teaching their students was Justice-

(However, the values that were concentrated and emphasized in one group were those that were lacking and necessary for oneself. It was a time when the Wulin's Zheng\footnote{'Righteous', but in wuxia more commonly translated as 'Orthodox'} factions was also quite rough.)

-If the character 'justice' is included, isn't it too old and outdated?

If you just flip the letters\footnote{正義 to 義正}, it felt completely new, but if you use a name that you were already familiar with, you're more used to it.

Of course, at that time, Wulin was also somewhat self-reliant, and it was a time when either the master's words were right or you'd get beaten.

At that time, there was no one in the Wulin Alliance who could compete with the unparalleled martial arts skills of the Wulin leader.

In the end, they had no choice but to make a signboard, even though they were saying things that were full of regret, like, 'I think the Zhengyi Martial Study Academy was better'.

But in the end, the leader's foresight was right.

At that time, the Wulin Alliance was a relatively loose social organization and merely a channel of communication with the imperial palace.

Even though it was called Martial Study Academy, it was just a place where young students were gathered together for a semester to promote friendship and invite high-ranking officials of the imperial family to get to know each other.

As the spirit of 'We're not strangers' in the Orthodox Wulin gradually intensified, the disciples of the already close and powerful Orthodox faction gathered separately in the Dragon Phoenix Assembly, so there was no reason to recruit for seasonal semester training.

Also, it was closely watched by the Imperial Family, due to its short distance, thus the purpose of the Martial Study Academy was changed.

It was giving the commoners a chance to build connections with the Wulin Alliance, which was already a semi-dominant force in  Jianghu!

Of course, it was only at the most peripheral level of the worldview and guanxi of Zhongyuan people, the level of acquaintances.

Nevertheless, if you go into Jianghu carrying the name of the Yizheng Martial Study Academy, you would receive countless benefits.

For example, you could somehow establish a small school in the Orthodox territory, and if you establish it in a independent territory, you might receive significant support.

Even if you don't necessarily have a title, it was an unspoken rule in the Orthodox Wulin that if you go somewhere and mention the name of the Yizheng Martial Study Academy, you will be accepted as a guest.

Well, even setting aside the benefits after graduation, the Yizheng Martial Study Academy was always seen as a great field of opportunity for ronin who were always looking for new skills.

This was a common imagination among ronin.

'Have you seen this person! I should take him in and make him my disciple right away!'

'Your talents may not be that great, but seeing your character and sincerity, I shall take you as my disciple!'

Well, these were the general thoughts.

Of course, the martial arts taught at the Yizheng Martial Study Academy were also at a level that even ronin should gratefully accept.

Even though they were common martial arts, unlike the ronin's, they either maintain their original form well or have been researched and improved to increase their power.

This kind of Martial Study Academy was opening!

A situation where ronin who already dream of a storm were gathering like a swarm of bees in Kaifeng.

In other words, it was a nightmare for the Alliance's staff.

The primitive and ancient Zhongyuan did not yet have a computer system like Qing homeland, and strict identity registration had not yet been implemented.

The flood of membership inquiries and even countless letters of recommendation were so overwhelming that you could fill a hole and enjoy swimming in it.

The staff of the Wulin Alliance were swallowing their screams, and the shadows under their eyes were only increasing due to the continued overtime work.

As days go by, family discord continues due to continued overtime work.

Sima Chunfeng, the youngest deputy commander of the Wulin Alliance (although it's not necessarily the position where the deputy commander's errand boy should be the youngest), was lying in the main hall on a warm spring day, basking in the sunlight and thinking.

Anyway, since they were trainees at the Yizheng Martial Study Academy, they can accept anyone just by looking at their character.

In fact, isn't character more important than talent?

Even if you graduate from the Yizheng Martial Study Academy and remain a third-rate student, most people will blame you, saying that it must be because you lack talent, and they would not dare saying that the Yizheng Martial Study Academy's curriculum was poor.

And if he were a person of character, he wouldn't be blaming the Yizheng Martial Study Academy in the first place.

So look at those foolish fools.

They say that if you're stupid, your body will suffer, so why don't you just pick someone based on their character? Aren't you just pretending to be busy and making things happen for no reason?

"I, I, I really fell asleep after playing around."

"Leave him alone. Has he been like this for a day or two? He's already finished his work, so he's probably just relaxing and lying around."

It was just as he said.

The great Samarang has already completed all his assigned tasks, and even if he had spare time, he would not want to get involved in such a foolish matter.

And it was already a familiar thing for ordinary people to be jealous and envious of geniuses.

Samarang picks up a red bean paste bottle while lying down and puts it in his mouth.

"That's why I'm even more annoyed. No, why was that expression on his face? He looks so pissed. It's like he's looking down on me."

"Fine. What's wrong with someone who's good at what they do? And was there anyone in the military who hasn't received help from Chunfeng at least once? You too, right?"

"Well, I guess I've become a bit more edgy since I've been working overtime all this time."

This was why everyday behavior was important.

Since I often helped with work and also often lay down after finishing my work, I was used to it and no one bothered to pick a fight.

Anyway, it looks like Sima Chunfeng was spending a leisurely time in the military palace, on the main hall where everyone can see him.

In reality, he was still working with that brilliant mind. (I think.)

Come to think of it, it's okay to just roughly judge the character of the trainees.

Unless you're really stupid, you wouldn't do something so foolish as to put up a sign for the Department of Political Science and Technology.

A person's status was important, and if he had trained in the martial arts academy of the Jeongpa martial arts world, even a worthless person would try to appear as a decent swordsman in front of others.

So, how can we make the opening of the new Yizheng Martial Study Academy a greater achievement?

Sima Chunfeng's work must always be the best in Zhongyuan, so he must produce the best political and military academy and the strongest officials of all time.

To do that?

Suddenly, a brilliant idea flashed through Sima Chunfeng's mind!

If we hire better talent, we will inevitably produce better results.

However, in order to attract talented people, you must attract them with greater charm.

So, what if you had the opportunity to become friends with Sima-rang, the current leader of the Dragon Phoenix Assembly and the future leader of Wulin?

If the successors of the less outstanding old and young generations also step forward, the effect could be half as interesting.

Sima Chunfeng suddenly raised her upper body.

Then she took out a piece of paper from her pocket and began to write in one stroke, quickly filling up the entire page.

It was a Military Division situation where people gave up their daily routines and made overtime a part of their daily lives due to their already overwhelming workload.

And now, the Military Division's workload was increasing even more.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Originally, Qing's usual itinerary up until now was to stop by Zigui, rest for a while, have dinner, and then go home, to her sweet home.

But.

"If you're here, why don't you just spend a night before you go? Are you just going to eat and then leave? You're so cruel, you know."

Cui Liwen, who had been increasingly upset whenever Qing did that, seemed to be extremely upset this time.

That's because Cui Liwen has evolved from a father to a grandfather.

"Hey, Ciyu, don't you want to eat some more snacks before you go? Grandfather has already ordered a bunch of snacks. They're pickled with honey-like jujubes from the western region, and they're out of stock, so even the Emperor can't eat them."

"Gulp." "Gulp."

At that, Ciyu swallows her saliva.

For some reason, the sound of swallowing saliva that resonated from two places.

Qing had no choice but to declare defeat.

Absolutely not, the honey-like dates from the West, definitely the dates, anyway absolutely absolutely absolutely not because of the date palm cookies.

The reason why she went up the mountain after dinner despite Cui Liwen's disappointment was because usually the master was there.

She couldn'just slept down there in Zigui when the Divine Maiden Sect was so close.

\textit{Since Master would be staying in Qinghai for a while, wouldn't it be okay to ease Granmp's mind a little this time?}

\textit{That decision has nothing to do with the snacks that even the Emperor cannot eat because there were none.}

"Well, then I'll just eat until tomorrow morning-"

"Huh. Only times like this should you be diligent. Why don't you just wake up slowly like you usually do and eat a hearty breakfast and lunch before you go?"

"Hey, Gramps, too. That's what I meant. Um, I need to get out and about after dinner. Should we go to the market or something?"

"Oh, are you okay?"

It would have been better if that cheap guy hadn't gotten involved here.

"Without an eye, you only have half the perception."

"What if both of you were dead? Can you protect everything you hold in your hands?"

It seems like the two of them aren't on good terms.

Well, it wasn't anything particularly strange.

It'd be strange that the former dog-like boss and the former subordinate were on good terms.

In fact, even when Cui Liwen was in the Demonic Cult, he didn't like the Supreme, but now that he had left, it no longer matter if he's being rude and he didn't even need to worry about it.

Yi-mei automatically followed along, and Xue-i-ri also quietly took the seat next to her, making the evening market a rather hectic party.

However, the relationship between the group was a total mess.

Didn't Qing Man-ha take on the roles of Ciyu's stepfather, her son Hosooin's stepmother, her father Hosooin's daughter who had dementia, and her stepmother's younger sister?

When you turn it into a group, it was a strange family tree with strange arrows drawn all along the line, it was the birth of a very strange family tree.

On the other hand, it was ambiguous to call going to the market a sightseeing tour.

Almost all the stores in the market were either affiliated with the Xuega Sanghoe or had received investment from it, and half of them were the property of the Xuega Sanghoe.

And everything in Xuega Sanghoe, including human assets, including the right to life and death, belonged to Qing.

So, it was more like a business inspection than a market tour.

Anyway, Qing didn't know.

Ciyu received so many gifts that Jian Buxi was carrying a bundle (since the employees of Xuega Store were now offering snacks to Ciyu), and Cui Liwen also looked quite satisfied.

There was just one flaw.

\textit{Hmm. Is it really necessary to buy souvenirs from the local area when you travel somewhere? They sell them all at Zhigui.}

\textit{Even the quality look better?}

Wherever Qing went, she brought back a lot of gifts for the disciples of the Divine Maiden Sect.

But looking at the Zigui market, um.

\textit{What should I say?}

\textit{It feels like I went abroad and bought that specialty product and came back with it, only to find it being sold at the convenience store in front of my house.}

\textit{But that doesn't mean I can buy a travel gift in front of the house and give it to them, and it would be strange to buy something from far away that was sold in front of the house and give it to them.}

The next day.

This summer was going to be a very hot one at first glance, but the sun has been shining brightly since early spring and the temperature was so hot that it seems like the scorching heat was already visible.

And Ciyu was finally able to discover one of her adoptive mother's strengths.

Coolness!

If Qing had known, she would have teased Iri a bit, saying that she had already found out her only advantage and that it was a shame that there was nothing left to find.

Anyway, even in the hot spring sun, Qing's steps as he climbs the mountain after eating a hearty breakfast and lunch were energetic.

Well, isn't the most rewarding thing about becoming a master of Hanseobanjibanchim the fact that my constitution has changed to one that was less sensitive to the weather?

As I climb up Musan, the peak of Shinnyeo Peak juts out over the high ridge.

"Ah! What is it!? Even though the sun is past its zenith, I can feel this intense glare!?"

"No! That can't be! The Grand Master, no, the Great Master, no, the Great Master, no, the Great Master, isn't coming at this hour! He's the one who always comes after the sun sets to replace the sun!"

"So, am I dreaming? Ah, if this was a dream, I hope I never wake up. Life is fleeting, a fleeting dream."

"No! Siliang, did you die standing up?"

"That can't be! This Tae Siliang, I can't die until I eat the candy that Grand Junior Master gives me!"

"As expected from Grand Junior Master! Now even the dead can be brought back to life!"

Qing tilted her head at them.

\textit{What? Siliang with Lianshu\footnote{戀書; lit. 'love letter'; Yeonseo in the original text} again?}

\textit{Why are these guys always stood guard?}

\textit{Is the main gate guarded 24/7?}

\textit{Or are these guys not disciples but hired mercenaries brought in as guards at the main gate?}