\chapter{Heaven and Earth Simp (5)}

Ciyu's eyebrows curved into an eight-character shape.

Even without that, there were dark shadows under her eyes, so she hunched her shoulders and pulled her neck in, making her look truly pitiful.

"No, why are you scarying the baby? Oh my, look how shriveled she is."

"No, I don't? So what is this guy?"

"Ciyu. She's my daughter."

Chen Changming's eyes opened wide at that.

Eyes wide open, pupils shaking, lips half-mooned. If she had been drinking fruit tea, it was an expression that would have made her slurp it down.

Then Chen Changming asked urgently.

It was a question that was almost like a rush.

"W-who's the baby's father?"

"Me?"

"……?"

"Me. Ximen Qing. Heavenly Blossom Sword. The genius of the end of the century."

"Who is the child's father?"

"I told I am. Im' Ciyu's Dad, right?"

He nodded with his neck shrunken.

Chen Changming stutters and asks again.

"Then what about Mom?"

"For now, Iri?"

"……??"

When introducing a child's mother, do you usually say 'for now'?

And what does 'now' mean?

So will mom change later?

Chen Changming was in chaos!

Then suddenly.

"Here. Bingseolhwa. What's your relationship?"

"Friend? Honorary member? My daughter's mother?"

"Stop joking. Seriously. What's your relationship? You're the father and mother of the child—"

"Why? Then, Changming can also be a mother."

It sounds like he's telling me to buy something.

Are you planning to make all the women in the world into mothers?

"uh?"

"Ciyu, this is Mom. Chen Mom. She might look around the same age as Ciyu, but she's actually much older."

"Mom again?"

"The more mothers, the better."

Ciyu nodded to him.

Although it's a bit strange, if it's Qing's words, I'll nod and look at him no matter what nonsense he says.

Chen Changming felt absurd.

The more moms, the better, after all, but before that.

It was annoying to hear that she's old, but before that.

"What kind of nonsense you're talking about?"

"What are you saying, kid? Are you going to refuse the honor of being my daughter's mother right now?"

"Huh?"

Chen Changming thought about it for a moment.

My daughter's mom. My sister was the dad, and I am the mom.

Although there was one strange woman involved.

My sister was my father, I am my mother, so we were a married couple.

Chen Changming's face turns crimson.

"Hmm, daughter? From now on, I'm your mother."

Chen Changming opened her arms awkwardly.

Then, Ciyu looked up at her father, who nodded, and awkwardly approached him and hugged him.

It was a touching moment of mother-daughter bonding, an awkward and sloppy hug.

It was the moment when another confusing line was added to Ciyu's genealogy.

With Chen Changming joining in on the yard cleaning, it's over in no time.

As a caretaker of Qing's house (unofficial, unpaid, passionate labor), he had a small house on a uselessly large lot, so how big must the yard have been?

Because he was Chen Changming, a true expert and authority on sweeping the yard.

Then, he sits down in the main hall of the Grand Elder Hall, takes a breath, and tells the story of the past.

Ciyu was nestled in her new mother's arms, and since she was holding her baby, they looked more like sisters than mother and daughter.

In fact, to the elders, Qing and I were not that different, and we look more like sisters with a lot of affection than father and daughter.

But no matter how you look at Chen Changming and Ciyu, they definitely look like kids one or two years older than each other.

For some reason, both of them were glancing at each other, as if asking for help, and it seemed very uncomfortable.

But don't help, don't help, just keep them hugging. That's how you become close, you know.

"So, Changming'er also wants to go to the Yizheng Martial Study Academy?"

"Oh. I want to go too."

It was an immediate answer without the slightest hesitation.

Of course, based on her experience in Mount Lao, Chen Changming secretly wanted to follow Qing's path in Jianghu, even if she doesn't force it.

I would say that this was a natural reaction.

Chen Changming joined the Yizheng Martial Study Academy!

"……For that reason, I'm going to the Yizheng Martial Study Academy as an instructor. Do you want to stay here?"

There wasn't really any story about Xue-i-ri, so actually, it's kind of ridiculous to say that Gun-i was an instructor. What do you teach and what do you learn?

However, it was equally strange that the friend left the house while leaving Xue-i-ri, who was like a guest visiting the friend's house, behind.

How much more pathetic would Gunyeong be than that?

"No. I want to go with you."

"Hmm. I guess I'll have to go and see what happens."

I heard from the master that this year's Yizheng Martial Study Academy has become even more of a hot topic because the disciples of famous families were taking on the role of instructors.

However, Xue-i-ri was still ambiguous.

The Bukhae Ice Palace was famous for being famous, but it was only famous for being the representative of the new martial arts world. Since they were barbarians who live against Zhongyuan, they do not have any particularly attractive connections.

In Qing's opinion, since he was one of the Five Flowers of the Martial Arts World, he should be able to stimulate the hearts of men.

But when you actually experience it, flirting was not a pleasant thing at all.

It's not a beauty trap to begin with, and even if it were, it wouldn't be a very pleasant experience for the person involved.

"Are you okay?"

"Yes, that's fine. But."

Xue-i-ri turns her head.

It was the direction in which Chen Changming, who had assumed the form of a wild brat from his past days, and Ciyu, who looked uneasy for some reason, were sitting.

A family gathering, to put it nicely.

To put it bluntly, and to put it more closely to the truth, it was a time of confrontation between the parties entangled in a dog family tree.

"Come here, Daughter. To First Mother."

"The first? Who cares?"

"Yes. Me. I'm First."

"I met Sister first, didn't I?"

Qing sighed deeply at him.

What the heck? Ranking? What the heck was that?

In front of the child, the mother says, "I like it, I like it, I like it, I like it, I like it," and the mother says, "I like it, I like it." Isn't this the behavior of adults in their twenties that you just can't believe?

Of course, they were still very young, at least compared to college students in their hometown.

"What does it matter whether you were first or second?"

"Does it matter?" "No."

"Whether it's the main wife or the concubine, there's only one child left. What's the point? What's important was the child's feelings. Why bother with rankings and playing military games? The closest mother was important."

The difference between a wife and a concubine was based on the status of the children. If there were no children, then the one who was favored was superior.

"Then-" "Well, then-"

"Stop it. Don't even think about asking Ciyu. It's a burden for the child, since she's not that clever. Come here, Daughter."

Ciyu moves to sit on Qing's lap.

As expected, it seemed like the lion was very uncomfortable with him wrapping his neck and burying his head in it.

It was the exact opposite of Qing's intention.

I thought I would become a very strict, serious father who scolds his children and protects them, a father who was truly the most fearsome and old-fashioned in the world.

It's because mothers were so stubborn.

"Well, maybe you need a soft and fluffy mom? Well, I guess Yi-Mei would be the best."

Come to think of it, no matter how many times I tell my mother, there were only faces that say she's not ready yet.

It seems likely that Young Lady Mo Yong, who has grown up so much, will become the most comfortable mother.

Then, Xue-i-ri and Chen Changming both realized it at the same time.

This was just the beginning!

The two of them intuitively realized that the genealogy was not even half complete.

Come to think of it, wasn't the idea of increasing the number of mothers something I had just casually suggested, as if I were going for a walk around the neighborhood?

Just by looking at her, you can tell that she's planning to leave it to all the women she knew.

And there weren't only one or two women that Qing knew.

Chen Changming thought.

'This woman isn't particularly dangerous. Her gaze doesn't seem impure, but rather resembles a large dog. The only danger is the physician'.

Xue-i-ri thought of a situation she didn't like.

It was a scene where the Tang woman holding Ciyu looked at her with a crooked look, and the two of them laughed at her with rotten smiles at the same time.

Their eyes meet.

It just so happened that there were one or two people with the same look in their eyes.

The two nodded at the same time, as if they were trying to make a deal.

It was the formation of an alliance.

It may be unfair to Tang Lan-Ah, but this was why there was a wisdom of life that has been emphasized for a long time from our ancestors to the present, that people must be careful about their daily behavior.

After that, a comfortable time followed.

Of course, Alliance's request was to join as soon as possible.

The attached letter states that they will first screen out the candidates through letters of recommendation and documents, and then proceed to the next round of tests.

If I had to say, it's a process that could be called a document interview for a large corporation. In the first place, isn't the qualification for applying to the Yizheng Martial Study Academy only for 'those who are righteous and seek to uphold justice'?

So, since applications were pouring in from all over the martial arts world, it was only natural that this process should be followed.

They basically said that they would test the candidates who had been filtered out once, so if it was okay, wouldn't you join quickly and help with the testing process? The letter said that it was an 'opportunity to fully demonstrate' the 'work that only blasphemous geniuses who can see through the very essence of people should do.'

I wonder if Qing has ever done any instructor work there.

So, it was also an opportunity to join in advance and learn the teaching methods of experienced instructors.

Of course, there was no particular reason why Qing couldn't set off right away.

Since Master isn't here, there's not much to do even if I stay at the Divine Maiden Sect.

It wouldn't be a bad idea to give Ciyu some time to enjoy the countless handshake and hug requests that come flying in from the Divine Maiden Sect disciples due to her explosive popularity.

But, well, it's not like the Divine Maiden Sect will run away, and there's still plenty of time left after the end of the Euijeongmuhak Hall, so it doesn't really matter if it's not now, right?

But unlike Qing, who had superhuman stamina, Ciyu was still a child.

We were beings who need time to eat well, sleep well, and get rid of the accumulated toxins.

You might wonder what kind of aftereffects it was when you haven't even walked a few steps on your own, but when people leave home, they feel nothing but hardship and inevitably, fatigue builds up.

So seven days.

It was a time when Qing just spent her time at the Divine Maiden Sect, just eating and playing around, lying around and just lounging around.

'But why seven days?'

This was the question that Chen Changming and Xue-i-ri had when they heard that they would be leaving in seven days.

'Come to think of it, Qing tended to measure time in seven-day increments, why is that? Does she like that particular number?'

Well, the act of grouping seven days into one week was what the Westerners claimed when they said that their creator worked six days and rested one day.

If the people of Zhongyuan knew, they would be wronged.

'Six days of work and one day off? Wow!'

For the people of Zhongyuan, there was no such thing, so they work yesterday, work today, work tomorrow, and work until their death.

'Our Ban-gu created heaven and earth after eighteen thousand years, so does that mean we have work for eighteen thousand years and rest for one day?'

Anyway, the seven days and nights ended like that.

"Your Majesty, please take care of yourself!"

"Sa-suk, have a safe trip. Be careful when you go to sleep."

The swarm of female disciples, almost as many as the entire congregation, waved their hands and saw Qing off.

Now it was clearly spring in full swing.

It may be an unusually hot spring, causing people to feel a sense of crisis that they will not be able to come to their senses this summer, but it seems that the spring flowers were only happy with the bright sunlight.
