\chapter{Heaven and Earth Simp (4)}

"Oh, that kid's going to the Divine Maiden Sect? Is she the youngest? For a youngest, she's very, very young. Wow, that's lucky. He's coming in as a sire instead of a sire."

"Hey, our youngest sister, how dare you be held in the arms of the Grand Prince, and how were you so proud of your lineage? You're saying there's no such thing as a knight's demise? You bitch, you demigod!"

"Oh, she's Ximen Ciyu. I decided to make her my daughter. I told Master about it. But she's not an initiate. She's just my daughter."

"Then, since you were the daughter of the Grand Prince, Grand Prince? The moment you saw me, you were so happy that you thought a noble person was coming!"

"Ah, the knight-errant was me. Lianshu, you two-year-old, you idiot! Sasukjo, instead of this ungodly millennium, I'll show you something. A fantasy-"

"Oh, it's me!? Do you feel like I should do it?"

The two were still noisy and chatty.

Aren't these two, among the three great disciples, the ones who were acknowledged to be the ones who stick together the most?

Being recognized means that people will ask you things like, "What were you doing alone? Why were you alone? Where did Lianshu/Siliang go?"

To that extent, it can be said that they were more than recognized as official best friends.

"You guys, you plan on talking until I put something in your mouth?"

"Aaaaah, I'm going crazy."

"Aaaaah, hehe, hey, gosh."

So, when you pass through the main gate of the Divine Maiden Sect Gate, all the third/second/first generation disciples you meet were in an uproar because they all say that they heard the cute Sasukjo/Sasuk/Samae.

Especially, the higher up you go, the more likely you were to become agitated. Now, how cute would a green-eyed brat who knows how to flirt as a proper middle-aged woman look?

In fact, the attitude of saying "pretty" was something that children tend to notice first.

Ciyu, who had been hunched over the Divvine Maiden Sect and had her neck tucked in with an anxious look in her eyes, was now looking around with her head turned around with a characteristically rotten gaze.

"Oh, Sister Xue is here?"

"You're here?"

Xue-i-ri was now treated as an honorary priestess, so no disciple was surprised to see her.

Perhaps she felt the same way, as she found her way to the guest room without any guidance.

And then climb up to the Shinnyeo Peak and go behind it.

When I turn the corner, my sweet home, the one I always miss, instead of a shabby house, greets me there as it always has.

Of course, from now on, Qing had decided to stay in the Taesangmunjujeon, so waiting would all be in vain, but anyway.

"Here we are. This is Daddy's house."

"……?"

Ciyu's eyes shook slightly.

As if asking, 'Really?'

Since she had only seen Qing living in luxury and receiving lavish treatment here and there, she seemed to find it hard to believe that this small house, with only one room and a half kitchen, is her Dad's house.

It seemed like Changming wasn't there yet, as it was a little past lunchtime.

When the sun was up, Changming trained, picked up firewood and wild vegetables, cooked, cleaned, and do other things for the Divine Maiden Sect, as the Divine Maiden Sect disciples were required to do their own work.

It would be impossible to just manage and protect Qing's tatched house like a Shizi\footnote{Chinese guardian lion statue}.

Qing, who had gathered the few clothes he had left in the dungeon, suddenly draws his sword and carves a phrase on the floor.

-Ximen Qing was here.

\textit{Hmm, what was it? Where have I seen that phrase?}

It's a phrase that seems to express the sorrow of someone who has already failed to adapt to society and has no place for himself.\footnote{A reference to a particularly depressing scene in 'Shawshank's Redemption' movie.}

\textit{I've adapted well and my place was fine.}

Qing adds a line below it.

-Are you dissatisfied? If so, come to the Grand Elder Hall, kid.

After packing her belongings to move out and adjusting her clothes, she went to the Grand Hall.

Wang Ju-hee, who had become even more plump, welcomed Qing with a very warm smile.

"Yes, you're back. However, Master is away on urgent business. She said she was going to Kunlun. Did you happen to see her?"

"Yes, Master will stay there for a while. As for what happened—"

"Youngest Sister, before that, shouldn't you introduce me to our lovely little guest. She's so bright and cheerful—"

Wang Ju-hee quickly changed her words when she saw Ciyu's rotten eyes and the dark shadows under them.

"-I don't mean to be rude, but oh my, how much trouble has that child already been through?"

A look of regret spread across Wang Ju-hee's eyes.

It was not uncommon for a disciple of the Divine Maiden Sect to pick up a girl who has nowhere to go.

And it was easy to guess that the world of the children brought in that way was not so easy.

"Oh, this is Ciyu. Ximen Ciyu."

"Ximen? Could it be that Youngest Sister is no longer the youngest? Did Youngest Sister bring a new Youngest Sister?"

"That's not it. I've decided to adopt her."

Wang Ju-hee looks surprised at that, but then nodded seriously.

"Since you said you met Master, isn't that already a given? I don't think Youngest Sister would have thoughtlessly passed on her surname."

"Yes. As for what happened—"

Qing told the story of the Kunlun Sect.

The Xizang's bandits, suspicious lamas, and the machinations of the Blood Cult.

"Those Blood Cult guys… What a world this is becoming. These are truly strange times. I think we need to tighten up discipline a bit. And drastically increase training hours."

"Oh, if you do that all of a sudden."

"It's not just because of what Youngest Sister said, but because it seems like Jianghu is once again facing a dangerous period. It was the same during the last Wulin tournament, and the constant mention of the Blood Cult… hmm, it doesn't bode well."

"Hmm."

Qing kept her words short and quietly expressed her condolences.

The words of the Sect Leader were not wrong, for it was true that the situation was unusual, from the martial arts competition to the Chen family, Mount Lao, and now Qinghai.

It may be a bit difficult for the disciples who were caught, but if something big happens, they will save the blood that will flow in the future as much as the sweat they shed in the present.

Or maybe? Then, all those training sessions were precious times that become flesh and blood.

As expected, the agui and seosun fit perfectly together.

In the hometown of Qing, it was also called Adari.

And while we're at it, I think it would be a good idea to make some hellish training plans with Ciyu.

"Then, can I help you with the Third-Generation disciples training?"

"Thank you for your kind words. Ah, there's a mission letter from the Alliance for Youngest Sister."

"Oh."

Wang Ju-hee grumbled as she handed Qing a letter with Alliance's seal on it.

"Aren't those Wulin Alliance bastards just using the Divine Maiden Sect for their own gain? What are they doing to a kid who's just finally back? It doesn't matter if you do it or not, and there's nothing much to gain for our sect, so if it's bothersome, you can just throw it away."

"Well, I did it once last winter, but other than that, I've been traveling around for my own personal reasons. Honestly, the Wulin Alliance missions aren't that arduous…"

Suddenly, Qing remembered the hardships she went through back then.

Of course, the Wulin Alliance was wronged here.

The great fighting spirit of the Green Forest and the military was due to Qing's shallow intention to take a shortcut, and had nothing to do with the mission from the Alliance, so it was simply a hardship that Qing had incurred herself.

"Still, the mission itself wasn't that difficult. Well, let's see."

Qing opens the letter.

The first thing that comes to mind was a rather flowing brushwork.

Qing's handwriting was a calligraphy recognized by all, but to Qing herself, it was nothing more than a boring and stiff regular script.

Of course, its greatness can already be said to have been proven by the fact that it was the standard script used in Qing's homeland for hundreds of years.

But the handwriting in the letter was so slender and elegant and has a cute charm, so it's not that hard to read, but anyway.

\begin{quote}
	To the only rival of this Samarang, Heavenly Blossom Sword.

This loneliness, frustration, and despair felt while looking down on ordinary people from the high heavens, containing the sorrow of a superior being.

You would understand this overwhelming sadness.
\end{quote}

It's quite unusual from the beginning.

\begin{quote}
	If we, the supreme geniuses, were born into this world, it was to enlighten and awaken those ignorant commoners.
\end{quote}

Qing lowered his gaze at the useless sound.

\begin{quote}
	-So, as an instructor at the Yizheng Martial Study Academy, it was time to educate and enlighten the followers of the Jeongpa martial arts world and also fulfill the duty of a superior being who saves those ignorant beings… 
\end{quote}

Qing just blurts out some dog barking.

"They told me to become an instructor at the Yizheng Martial Study Academy. Hmm, Yizheng Martial Study Academy? I think I've heard of it somewhere."

"Ah, right. There was a lot of excitement when the Yizheng Martial Study Academy opened. Apparently, it's going to be especially grand this time. If it's Youngest Sister, you're more than qualified to be an instructor. You're a true master of the Unrestrained Realm."

Wang Ju-hee smiled happily.

It's not some mundane mission, but rather the position of instructor at the Yizheng Martial Study Academy.

This was a recognition of the level of blind faith that Qing was a master with such rigorous study that he can teach others, and it was also a recognition that the world will soon have when this news spreads widely.

From the perspective of the Divine Maiden Sect, it was an opportunity to make a name for themselves, aside from the impure reason of being a mysterious sect of women and a sanctuary for Geumnam.

And it's not like she'd be on a business trip to go somewhere and get some dirty food, so she just need to quietly work as a martial arts instructor at the academy and be treated like a teacher. Wouldn't that be enough?

However.

"I think I'll probably reject it this time."

"Huh? Why? It would be a good opportunity, wouldn't it?"

"Ciyu need to learns martial arts, and I want to teach her earnestly as her father and master."

"Then there's nothing we can do. I'll send them a reply by messenger. Hmm? Right."

Wang Ju-hee clapped her hands together as if a good idea had occurred to her, and changed her words.

"They say the Youth Division is opening this time, so how about we just have Ciyu enter the Youth Division at the Yizheng Martial Study Academy?"

"Boys' Club?"

"Wouldn't it be much better for the child if she could practice with other children her age? Thanks to the generous generosity of the Xuega Sanghoe down here, there haven't been any poor children taken in to the sect lately. Even if she grows up among her older sisters, she'll still need friends her own age."

"Oh."

Qing vehemently agreed with her.

Then, all you have to do was ask for the position of instructor for the Youth Division.

Since it was a physical training based on the past, wouldn't it be a truly effective training for the new sprouts of our martial arts world that were just starting to grow?

Wang Ju-hee adds to this.

"Even without that, each sect has been requesting that we admit disciples who can study independently. They need someone to take on the role of leader. I was wondering who to send, but if you say you're going, Changming will probably follow. Since you're already a disciple who's always looking for a partner, I think it would be nice if the three of you went together like that."

The Grand Elder Hall was neatly organized.

The always neat and tidy Master must have cleaned up everything before she left, but even if she hadn't, would the disciples, the same generation with Qing, have neglected the Master's residence?

So, the moment when Ximen Surin asked her to come in and manage the empty building was proven to be nothing more than an excuse and was based on her own selfish desires.

However, it wasn't maintained enough to be cleaned and used every day, so Qing simply unpacked her belongings and went straight to cleaning.

Cleaning was done from top to bottom, from inside to outside, following simple principles, and the last step was to finish cleaning the building and sweep the yard.

And the moment Chen Changming came, it was right when Qing was sweeping the yard, and Ciyu was offering to help with a broom as tall as her, but instead, she was messing up the yard and causing trouble.

And as soon as Chen Changming discovered Qing, she said this:

"What is this again?"