\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (5)}

Of course, the essence of existence had not changed.

And the essence of Jian Buxi was to be Crutch No. 2.

The Heavenly Demon Divine City was a city composed of nine districts.

The nine districts were intuitively named, as cities in Zhongyuan typically were, divided into the Central District and East, West, South, and North Districts, plus other obvious names.

The Bliss Palace was located at the end of the red-light district in the East District.

"So, Junior Sister, where should we go sightseeing first? Is there anywhere you want to visit? Shall we go look at some ornaments? Should I buy some throwing binyeos too?"

"That's not my business. You do whatever you want. As for me, I heard there's a place called Stove Street in the Northwest District."

"Eh? That place is dangerous, though?"

"Dangerous?"

"It's a neighborhood where non-believers live, so patrollers don't go there at all. It's a complete lawless zone."

Qing did not understand.

To Qing, the entire Heavenly Demon Divine Cult seemed like an absolute shitfest where the strong reigned supreme.

However, there was one thing that concerned her.

"Patrollers? Officers? Is there an official authority here, like the government?"

If such people were roaming around, it would be bothersome to go out at night.

Qing herself had been caught several times before.

It was because most of the people in South Korea did not understand that they shouldn't be out at night.

In fact, Qing still didn't understand.

But it wasn't just Qing; all Masters thought the same way.

When one reached a higher realm, they suddenly couldn't comprehend that nighttime walks could be dangerous.

"Officers? Official authority? Government? Ah, right. You're from Zhongyuan, right, Junior Sister? We don't have an official authority! Or a government! Our patrollers are members of the cult. Sure, in the Zhongyuan, they say those officers extort money and kidnap children to eat them, right? We need to quickly liberate the Zhongyuan from the oppression of the officials and Wulin in order to-"

"Enough. Forget it. Rather than that…"

Qing cut off Jian Buxi's nonsense straight away.

"Are there many patrollers? Do they also catch people roaming at night here?"

"At night? Why would they be there at night? Patrollers get off work when the sun sets."

"……?"

Qing was momentarily speechless.

\textit{Wasn't patrolling supposed to be done at night?}

During the day, all that happened were minor scuffles among the people of Wulin, so there was nothing for the officers to do.

Thus, maintaining public order on the authorities' side was mainly about keeping guard at night.

At any rate, this was good news for Qing, who was conducting a preliminary reconnaissance for her night outing.

"Alright, let's head to Stove Street. What's to worry about when there's a Master here?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And that night.

Qing, with her face tightly wrapped, jumped over a wall.

The zero-gravity steps of the Yue Maiden Footwork truly displayed its worth.

A narrow yard of one span1 and a cozy house with two rooms.

Qing carefully removed the door that she had broken by grabbing and crushing the hinge.

And right as she entered-

Something got caught on her ankle.

A thin thread, barely visible to the eye.

A trap!

Qing immediately flung her body.

And surprisingly, nothing happened.

No arrows or needles flew at her, nor did any loud noise announce her intrusion.

\textit{What is this?}

\textit{A trap with nothing to show for it?}

\textit{The fuck. What's up with this unsettling feeling?}

Qing stood up feeling rather unnerved.

It was at that moment.

"Who is it?"

The sliding door creaked open, and a middle-aged man appeared.

It was a strange sight.

After all, his hair and face were dripping wet.

He didn't seem to harbor any hostility.

As such, Qing decided to first ask what she was dying to know at this moment.

"Uh, were you washing your face or something?"

"Did you not pull the string?"

The middle-aged man pointed inside with the blade in his hand.

On top of a table that was awkwardly close to the bed, there was an overturned water bottle.

"Is it structured so that pulling the string douses you with water?"

"That is correct. But speaking of, who are you? Coming at this hour, at that."

"I heard you have some good martial arts, so I came to ask for some. Are you perhaps the person known as Xue Ga?"

The middle-aged man replied.

"You probably heard the name Xue Ganom \footnote{Seol Ganom (설가놈) in the original text. Ganom (가놈) has no equivalent in the Chinese script, so it's left as it is}, not Xue Ga. My surname is Xue, and my name is Ganom. It is rare, but it is a proper Northern Sea-style name."

"Oh, your name is Xue Ganom…"

It was pretty interesting, but the name of a mere villain was not what was important.

"Anyway, as for the Ice... Godly Asura Demonic Arts? Whatever it is, if you hand it over obediently, there won't be any bloodshed."

"It's called Heavenly Ice Sura Demonic Arts. You seem to be a robber that is quite lacking in the head, ho?"

"Anyway. Hand it over nicely before things get very painful for you."

The man asked back.

"Why do this? If you wish to learn, you could just become a disciple, could you not?"

"I already have a Master."

"Mm? Aren't you a Demonic Cult disciple? Demonic Cult disciples would do anything for martial arts, do they not? Even if it means selling their own parents."

"Ah. I heard about that. Anyway, that's not my style. I don't do that kind of stuff."

"That style, is it? I see."

Xue Ganom nodded.

Qing was taken aback.

"Excuse me, but aren't you too relaxed? A Master has invaded, you know? I'm at the Mid-Stage Peak Realm."

"Does being nervous mean you'll spare me?"

"Probably not?"

"Then why bother?"

"Huh, I guess that's true."

Qing agreed.

"Anyway, it would be better if you hand over the Secret Manual or the Sutra immediately. Otherwise, it will be very painful for you."

"That is quite a pity. Since unfortunately, torture won't work on me."

"I bet once you experience it, you'll realize, ‘Ah, torture isn't something to take lightly,' you know?"

"Look at this."

Xue Ganom lifted his long bangs.

On his forehead, a brand appeared.

"The Demonic Cult bastards branded me while I was sleeping. I only realized it the next morning. That is why I installed the water bottle. After all, my body is one that does not feel pain."

"Uh, seriously?"

\textit{He can't feel any pain?}

\textit{Then, I mean, that's a bit... Isn't that kind of a deal-breaker?}

"When a person cannot feel pain, this is what happens. If you do not know pain, you do not feel fear. Does this seem normal to you?"

"Nope."

"Right. Even so, do you still want the Heavenly Ice Sura Demonic Arts? Once you start cultivating it, there is no going back. The more you amass its Qi, the more your senses dull, and it will result in this."

This was the biggest problem with the Heavenly Ice Sura Demonic Arts.

Qi Accumulation is a habit that a martial artist carries for life.

As such, in the end, they will inevitably lose all their senses upon cultivating this martial art.

From Qing's perspective, however, it wasn't a big issue.

It would all be fine anyway once she reached the Grand Star and maxed out her Ability Points.

Rather, she was more worried about the Heavenly Ice Sura Demonic Arts with its Red Border being less effective than the Blissful Maiden Arts with its Golden Border.

"That's something I'll handle, so just hand it over obediently."

"Understood."

Xue Ganom immediately agreed to Qing's words.

"…Really?"

"However, there is a condition."

"What is it?"

"Spare my life."

Xue Ganom shamelessly begged to have his life spared.

Qing was rather taken aback.

"Didn't you just say you were dull and abnormal and whatever? You acted like someone ready to die, didn't you?"

"I would not have crawled into this remote Demonic Cult if I did not want to live, even if it is a life that does not seem like truly living."

He was a strangely logical Demonic Human.

"Um…."

Qing enjoyed killing or torturing villains.

Because it was okay to do so to evil people.

But it wasn't like she was some OCD patient who just had to fuck up every last one of them.

Nor was she an addict who couldn't resist killing.

She simply didn't bother to restrain herself. That's all.

"Then instead, can you tell me about any nearby, weak, killable, villainous bastards with pretty convenient martial arts?"

"There's an assassin called the Smiling Fiend living right next door. He is only at the beginning stages of the Peak Realm, so there is no way such a grand title could be given to him. It must be a mixture of exaggerated boasting and a bluff."

"Left side? Or the right side?"

"Looking at my house from its front door, he is on the right."

"And his martial arts?"

"Being an assassin, he probably has some stealth techniques. If you intend to continue to rob others, you would need at least one technique that kills your presence, no?"

It was a logical and reasonable opinion.

Qing fully agreed.

"Alright. You pass."

"But, I do not have the Secret Manual. Even if I recite the Sutra, how can you trust that I am telling the truth?"

"I have this supernatural-like ability to detect incorrect Sutras, okay? So if you don't want to lose the life you've just managed to save, don't try any tricks."

"There is no need to worry about that. It is a cursed Demonic Art anyway, so there is no reason for me to teach it incorrectly. Just do not come back and blame me later."

Xue Ganom then recited the Sutra.

Qing considered cutting off a limb if he tried any tricks, but the Martial Arts Window flashed, declaring its authenticity.

\textit{Aw man, too bad.}

\textit{But torturing someone who can't feel pain didn't seem that fun anyway.}

"Come to think of it, continuously reciting until you memorize it is quite the hassle. If it's hard to remember, just come back tomorrow. I shall write it down for you."

"I'm done already. I only need to listen to it once."

"You memorized all that in one go? How impressive. You will soon be like me, then."

It was hard to tell if it was a compliment or an insult.

So, Qing just ignored it.

"Anyway, keep it a secret that you saw me, okay?"

"What is there to boast about being blackmailed into giving up my martial arts? It's too embarrassing to even talk about. Ah. By the way."

"What is it?"

"Not only should you cover your face, but you should also bind those large breasts tightly. How many women are there in the Demonic Cult that has three heads? I am letting you know, so that you do not blame me if you are caught later."

"Ah, shit. That'll make me all sweaty, though."

However, it was a logical and reasonable problem with a practical solution.

Qing accepted the criticism.

"But still, well, thanks for the advice."

With that, Qing left Xue Ganom's house.

About one shichen later, she returned at the break of dawn on this summer night.

Xue Ganom, who had to wash his face again, appeared with an uncomfortable expression.

"What is it? Have you changed your mind already?"

"Nope. You gave such good explanations, you see. So, I was thinking. Can you perhaps introduce me to another weak but killable Demonic Adept with powerful martial arts?"

And then, the next day.

The Smiling Fiend, surnamed Wang, was found murdered.

His body was dismembered, with the torso, head, and limbs separated.

However, if it was just this much?

Then it was not yet shocking enough to attract attention in the Heavenly Demon Divine City.

At least not yet.