\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (9)}

The subsequent music lesson was quite enjoyable.

"Please, just once more, let's just try playing it one more time. Okay? You need to master it within a month. Please."

"Ah, there! There, on the calf, just now! Aeuhhh..."

Qing made a strange sound.

But it couldn't be helped.

Madam Kang's main specialty was the Guqin, a seven-stringed instrument.

As such, her grip strength was extraordinary.

Madam Kang was desperately massaging Qing's calves all while pleading with her to practice.

And that sight was watched by Assistant, no, Maid Soyeong with a smirk.

"Ah. That feels good. Teacher is truly the best teacher I can ask for. Look at how she massages the legs of her inconvenient student so well. It makes me feel all weak-hearted again. Hm, then shall we try playing another verse?"

Only then did Qing slowly get up and put the Fushen-di in her mouth.

Then she blew it with all her might.

Madam Kang ground her teeth internally.

She couldn't do it outwardly, of course.

There was no such thing as age or seniority in the face of the stick.

The frustration that Madam Kang felt was about to explode as she listened to Qing's playing.

The Heavenly Heart Harmony was a sorrowful and delicate melody meant to release the sorrow of lovers.

However, the Heavenly Heart Harmony that Qing played had a fast rhythm, with a majestic and precise playing style that was as rigid as a Mount Tai and more akin to a military march.

What was even more infuriating was something else.

She actually played it well!

The sound of the flute was said to be the cry of a beauty.

Basically, it should never be played like that.

\textit{But why?! Why does she play it so well?!}

\textit{And why does it sound good?!}

It was like creating a gourmet dish, unparalleled below the heavens, with rotten meat and rancid oil.

The musical perspective of an artisan who had dedicated fifty-five years to music was being shattered.

"S-Stop! That song shouldn't be played lik..."

"What the. Ehh? Did I mess up again? Oh dear! It seems like the teacher's incompetence made the student fail. Shouldn't the teacher who failed to teach be punished?"

Qing tapped the Fushen-di on her palm.

Madam Kang flinched but spoke without yielding.

"What I mean is, you played well! Very well! It's excellent!"

"Really? But it feels like I made a mistake somewhere, didn't I?"

"N-No. It was a flawless performance."

Qing nodded with a satisfied expression.

"I know, right? It does seem like I have a talent I didn't know about. It's all because the student is so outstanding, right? I should have put more effort into playing the flute during music lessons."

Madam Kang shed tears of blood inwardly.

\textit{What a vicious bitch. How can someone as wretched as her exist under the heavens?}

For reference, in the wide world, there could be filial sons who beat their parents, but there are no pieces of shits who would ever beat their teachers.

However, the law was far and the fist was near.

In fact, the fist became a law that transcended time and space.

Madam Kang eventually couldn't hold out any longer.

"Since we have mastered two verses today, let's conclude today's lesson here."

"Ah, just when it was starting to get fun."

Qing smacked her lips in regret.

"No. Anything in excess is not good. As such, you nee- will have to need some time to master what you've learned today. So, do not be greedy and..."

"Well. Okay."

Qing waved her hand as if she understood.

Then she sat cross-legged, straightened her back, and spoke.

"Then, show your respect to this esteemed student who attended the lesson and leave."

"……?"

"What are you doing? There is no teacher without a student. Don't you realize that I am the reason for your existence?"

"That, uh, the Fushen-di..."

"What about the Fushen-di?"

Qing growled with a smiling face.

"What's wrong with holding my own instrument? Ah! A mistake! Did this student make another mistake?"

"N-No. I meant, keep it well since it's precious..."

"Of course. Now then, show your respects and leave."

In the end, Madam Kang awkwardly bowed her head and hastily ran away.

After being hit about four times, Madam Kang had managed to teach two verses through endless massages, flattery, and pleading.

Had Madam Kang stubbornly stuck to her pride with a rigid nature, she would have been split vertically like bamboo.

In the end, she managed to achieve her goal, albeit a little, by hiding her true feelings and smiling servilely, didn't she?

She was a true teacher of the era, one who shouldn't be insulted carelessly as stupid and weak-hearted.

Qing stretched.

"Ah. That was fun."

Only then did Qing call up the Mission Window that had been flickering in a corner of her vision.

\begin{quote}
[Divine Cult Under The Heavens, War and Chaos of the Demonic Cult. The Middle Chapter. (Unknown)th Crisis]

Description:[You have become the key to opening the Heavenly Demon Tomb of the Divine Cult/Demonic Cult. Help the Divine Cult find the Heavenly Demon Spirit or destroy it to forever remove the most powerful force of the Demonic Cult.]
\medskip

Master the Heavenly Heart Harmony to gain the qualification for entry to the Heavenly Demon Tomb. Decide the fate of the Cult in the Heavenly Demon Tomb.

Righteous Karma) Destroy the Heavenly Demon Spirit

Heavenly Demon Divine Cult) Deliver the Heavenly Demon Spirit to the Supreme of the Divine Cult

Heavenly Slaughtering Star) Kill everyone

[This choice could influence everything below Heaven.]

\end{quote}

The conditions of the Mission Window were now somewhat understandable.

The main branch or storyline appeared when facing a major event.

And before encountering it, if a certain level of information about the upcoming event was obtained in any way, it would appear in advance, pulling this kind of shit.

Last time it was the Beginning Chapter, but now it's the Middle Chapter.

There would probably be an End Chapter as well.

Maybe even a Final Chapter.

But this time, it didn't particularly bother her.

Why?

Because the Demonic Cult motherfuckers are bad guys anyway.

Qing's eyes grew cold.

Now the rough goal was set.

\textit{First, prioritize looting the bastards with good Qinggong Techniques, mastering them to increase speed stats.}

\textit{And since the more Inner Arts the better, also loot those with decent Inner Qi Cultivation Techniques.}

\textit{Then go to the Heavenly Demon Tomb, break that thing called the Heavenly Demon Spirit or Horn or Hoof or whatever the fuck it is, and just leave.}

"Kekeke..."

Qing chuckled to herself.

After all, she had just made a veryyyyyyyyyyyy high-level joke, playing on the same pronunciation of the Western word for horn and the translated word for spirit/ soul.

\textit{Wow, it's such a funny joke.}

\textit{But there's no one to share it with.}

\textit{What a shame.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\begin{quote}

{\ttfamily Heavenly Demon Divine Cult Serial Murder Case.

Inner Hall Investigator Shi Hengheng\footnote{石哼哼. Seok Humhum (석훔훔) in the original text} reporting.
\medskip

First-day victims.

Tempest Walker, Wu Xiuxuan\footnote{Oh Sooheon (오수헌) in the original text}.

Cause of death was heart rupture. The perpetrator crushed the heart with their bare hands.

The entire body was also found with compound fractures.

The perpetrator tortured the victim while they were still alive.

First Disciple and Successor of Royal Demonic Path Clan's Sect Leader, Bo Yunzuo\footnote{Pa Unjak (파운작)}.

Cause of death was asphyxiation. The perpetrator strangled the victim with their own intestines.

The entire body was also found with compound fractures.

The perpetrator tortured the victim while they were still alive.
\medskip

Second-day victims.

Godly Thief of Undergarments, Yang Ling\footnote{Yang Ryeong (양령)}.

Cause of death was hemorrhage. The perpetrator split the stomach and large·small intestines, stuffing them with stolen items-mostly women's underwear-before roughly stitched it up and hung the victim upside down.

The victim presumed remained alive for about two hours before finally dying.

Outer Hall Covert Operations Division's Special-Grade Assassin, Number Eleven.

Cause of death was poisoning. The perpetrator flayed the victim's skin and alternately poured poison and antidote, then left them unattended.
\medskip

Third-day victim.

Divine City Defense Squad's Fourth Patrol Team Leader, Ye Lingji\footnote{Bam Neungje (밤릉제)}.

Cause of death was shock from meridian rupture.

**Important: Traces of the White Hand Demonic Arts found on the body.

Reexamination of the victims confirmed meridian rupture by the Penetrating Power of the White Hand Drought Poison.

It is presumed that the White Hand Witch of the Blood Cult has infiltrated Tian Shan Divine City based on the circumstances, requesting cooperation from higher authorities.

Furthermore, as there was only one victim today, it is suspected that there might still be another victim somewhere.

Afterward, received a missing report for the Sex Fiend of Jiangnan, Fang Daojun\footnote{Bang Dojun (방도준)}.

*Confirmed that Fang Daojun was killed by Jian Buxi, the Fifth Disciple of the Bliss Palace's Second-Grade Disciples.

Jian Buxi testified that Fang Daojun attacked first under the pretext of teaching Dual Cultivation, and since the victim's usual conduct was such, it was ruled as a legitimate duel.}
\end{quote}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing checked the new martial arts she had mastered.

From the guy named Wu Xiuxian, she obtained the Red Footwork Technique, Wind Steps, and a few other miscellaneous martial arts.

But why would anyone even practice a White Inner Qi Cultivation Technique?

\textit{If it were me, I'd be too embarrassed to practice it. Seriously.}

\textit{The bastard known as the Successor of the Royal Demonic Path Clan was quite something.}

\textit{I had such a fun time because he lasted so long, after all.}

\textit{After I kinda lost my shit about three times, my whole body was shaking so much that I almost couldn't make it back to the Bliss Palace and nearly just fell asleep.}

\textit{I was too excited. I should control myself a bit...}

In a hurry, Qing raised the Heavenly Ice Sura Demonic Arts to Four Stars.

As expected of a successor, he spat out two Gold Martial Arts, but only one was useful.

The Inner Qi Cultivation Technique, Blood Demon King Divine Arts.

The other was a Half-Sword technique called the Blood Shadow Thunder Lightning Half-Sword Technique.

\textit{Why, though? Why bother using a half-sword that only has one sharp side of the blade, with only half the power?}

Still, Qing registered it for now.

From that underwear thief, she obtained a Gold Footwork Technique called Thousand Li Flight.

He was a pathetic fucker who used a precious Gold Footwork Technique to steal underwear.

When she had sneaked in, he wasn't sleeping but instead sucking on women's underwear and shaking his stick.

So, she had filled him with underwear until he was literally about to burst, just as he wished.

There was also a ninja-like guy, using ninja-like techniques, so she almost missed him.

He started sprinkling a shitton of poison, so she returned it all to him. And perhaps he was deeply moved when she returned what was his? Out of gratitude, he passed on a Red Movement Technique called Black Shadow Stealth.

And last night, Xue Ganom's information was wrong.

He was supposed to be the previous owner of the Secret Manual of the peerless Qinggong Technique, Ghostly Shadow Ten Thousand Flowing Steps.

When she asked about where it was, he confessed that he spread the rumor and sold a fake Secret Manual.

And all that came out of him was just White, Blue, Blue.

She was so angry that she tried to hit him, but she failed to control her strength.

\textit{No, my precious time to recharge my happiness!}

And somehow, when that time was just gone with the wind, she felt somewhat… empty.

She thought she might have become exhausted.

It's so tiring not being able to sleep at night…

So, to boost her morale, she caught a Sex Fiend and handed him over to Crutch No. 2.

\textit{Ooooh!}

\textit{The first-row VIP seats to that viewing was fucking incredible!}

\textit{Wow, how would I even describe that?}

\textit{It's like on a completely different dimension from porn, though, of course, since there's actually a one dimension difference between 2D and 3D.}

\textit{But still, like… Wow, this, how, ooooh. Yeah, I can't describe it.}

\textit{I better catch another one for her next time.}