\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (1)}
	
The Bliss Palace Leader died during the transport of the prisoner.

When the news was delivered, all the elders of the Bliss Palace were engulfed in deep sorrow.

To be clear, Bliss Palace Leader Xian Yue was never a good leader.

Her personality was brutal, treating elders like maids and preferring to use her fists rather than her words.

On top of that, her greed was beyond ordinary, monopolizing handsome men or the occasional high-ranking prisoners that came her way.

Still, Xian Yue was the owner of the Bliss Palace.

And the owner of the Bliss Palace was the master of the Blissful Maiden Arts.

In other words, Xian Yue was a living Secret Manual capable of fully transmitting the Blissful Maiden Arts!

To be honest, the Elders would call Xian Yue Xi Shi Divine Maiden, but refer to her as Retarded Bitch behind her back.

Or, to be a bit more affectionate, a Motherfucking Bitch.

Everyone wished for Xian Yue's death.

However, they hoped she would only die after passing on her Divine Arts.

Thus, in their sorrow, the Elders asked.

'So, what about the Secret Manual?'

It was difficult to learn martial arts from just the Secret Manual.

However, it was better than having the martial arts disappear entirely.

Additionally, perhaps the Elders of higher ranks could at least research together and add new annotations if they had it.

Amidst their sorrow, a glimmer of hope flickered among the Elders.

But the Secret Manual was actually burned.

If the study of physics were highly developed in Zhongyuan, they could at least comfort themselves by saying that the Secret Manual still existed, transformed into heat and light.

However, Zhongyuan was still primitive, so they could only feel regret and sorrow.

True to the five stages of grief, the Elders soon entered denial.

'No! This cannot be real!'

'Something must have gone wrong.'

'No matter how much of an idiot or a Motherfucking Bitch that Retarded Bitch Xian Yue was, she wouldn't have carried the Secret Manual around, right?'

'If she had died with the Blissful Maiden Arts' Secret Manual on her, the Bliss Palace's ultimate technique would have been lost entirely.'

'No matter how much of a thoughtless and selfish bitch she was...'

But upon reconsideration, Xian Yue was indeed the kind of bitch who would do just that.

That Retarded Bitch really did cause a mess, didn't she?!

The Elders overcame the stage of denial with logic.

The next stage was anger.

'No, but why burn the Secret Manual along with Xian Yue?'

'I thought the Bliss Palace Leader was the only motherfucking piece of shit bitch under the Heavens, but it turns out there's a sky above the sky!'

'I will not let this unprincipled villain go unpunished!'

Angry Elders flocked to Qing, who had just settled in a corner of the Bliss Palace.

"Was it you? The vicious bitch who burned the Blissful Maiden Arts!"

\textit{What the fuck, who are these people?}

\textit{Why are they suddenly coming at me and cursing me?}

After briefly analyzing their demeanor and preferences, Qing deduced what the most provocative response would be.

Honestly, at this point, her natural talent of deduction was akin to artificial intelligence.

"Yes! It was indeed me!"

Qing declared confidently.

While the Elders were at a loss for words, Qing followed up.

"But who are these old aunties? By the way, shouldn't you take better care of your wrinkles? Do you think covering them up with makeup helps? Well, I mean, I guess there's nothing that can be done about aging."

\textit{Old! Aunties! Wrinkles! Makeup! Gasp!}

The Discipline Elder grabbed the back of her neck.

Qing's mouth harbored a terrifying tongue that struck precisely at the weak spot she had always been conscious of.

As she was already agitated and uneasy due to the loss of the Divine Arts, this was practically a fatal blow.

The Discipline Elder gasped for breath and eventually coughed up bright red blood.

The Early Stage Transcendent Realm Master's Qi and blood started running in reverse, leading to Qi Deviation.

As her Inner Qi leaked out, her once taut skin instantly wrinkled into the appearance of an old woman.

The position of Discipline Elder usually went to the strongest Elder in active service.

The same was true for the Bliss Palace, so following the demise of their Palace Leader, their greatest force had now also fallen.

"Woah. You weren't an auntie but a grandma, huh."

\textit{Woah. Not only does she have a lot of Evil Karma, but she's also very old, isn't she?}

Qing remarked on this mystifying sight of rapid aging that she witnessed in real-time.

Another Elder, shocked by the term grandma, also reacted.

"You, you bitch!"

"No, stop! Administrative Elder, calm down!"

The Training Elder, who was somewhat close to the Administrative Elder, quickly infused True Qi into her meridians.

The Administrative Elder narrowly avoided Qi Deviation.

Qing clicked her tongue.

\textit{Too bad. I could have taken out one more.}

At that moment, the Head Elder yelled at Qing.

"You! Do you know what you have done?"

"Didn't I kill your boss, auntie? Is killing a bitch that deserved to die a crime?"

Qing continued to provoke them.

But this time, it didn't work.

"Such things do not matter!"

Xian Yue's death was of no importance.

It was deemed as something insignificant.

Take note. This is why one should always be kind to people.

"How dare you burn the Divine Arts!"

\textit{Ah. It was about that?}

Qing briefly reflected on her mistakened understanding.

Even after hearing 'the one to die is in the wrong' following her previous murders, she still hadn't fully grasped the law of the strong.

\textit{What the hell? Seriously?}

\textit{Does the entire Heavenly Demon Divine Cult believe that shit?}

\textit{Then how does the organization even sustain itself?}

Suddenly, a sociological curiosity arose.

It was the profound liberal arts taught from a prestigious university that had made Qing a self-made blue-collar worker.

As such, Qing quickly lost interest.

After all, now that she thought about it, it had truly been a useless choice of the past.

If Qing could return to the past after beating Lil Window and returning to reality, she would major in big data instead.

After reflecting, Qing refocused on her target.

"What's so wrong with burning an evil Demonic Arts?"

The effect was outstanding.

"L-Look at that impudence! Just listen to her! How dare she!"

"Evil Demonic Arts?!"

The elicited women squawked, making pterodactyl noises.

Qing tilted her head nonchalantly.

"Eh, it's not?"

"H-How, how can you say such a terrible thing! The Blissful Maiden Arts are a proper Divine Arts! Even if we are treated as one of the Left-Hand Path...! U-Ugh, ugh."

The Great Elder staggered.

In the absence of the Palace Leader, she was second in rank.

Of course, Qing had no interest in that.

A new interest did arise, though.

"What? It wasn't Demonic Ar- Hoit."

At that moment, a palm flew, aiming for her cheek!

Qing instinctively grabbed the wrist.

"Let, let go, KYAAAAAH!"

It was the Training Elder, who had lost her temper and charged.

Qing's Black Hand, which was infused with toxic Black Slaying True Qi, penetrated.

The resentment of being treated unfairly met a timely and brutal infiltration.

As the meridians were torn apart, the Elder's wrist rapidly turned black and bruised.

Qing's strength was formidable.

Though the elder struggled to escape in surprise, Qing merely gripped the arm firmly and gently shook it.

Qing frowned.

"Agh, shit. I used Demonic Arts because you startled me. Do you know how hard I tried not to use it?"

"Guh, let, let go! Let go, I s...!"

"Wow, this auntie is funny, huh. Do I look like someone who needs to let go if you tell me to let go, and grab if you tell me to grab? Your manners are awful. Is that how you request someone? If you had politely asked me to let go, I might have conside- Hoit."

Qing also grabbed the other arm that was hurriedly flying at her.

Now, both of the Training Elder's arms were caught.

As such, the two women were forced to face each other.

Qing saw a number. Three hundred twenty-four.

\textit{Why is this place like this?}

\textit{Is it because the head is that Alleged Supreme?}

Qing squeezed her hands tightly.

Her grip was one that could crush iron.

The auntie's frail wrists were like tofu being squeezed and crushed, thus oozing through Qing's fingers.

"KYAAAAAAAAAH!"

The Training Elder screamed and staggered.

Her thrashing arms severed at the forearms, with blood spurting everywhere.

Amidst it, Qing trembled.

\textit{What is this? What the hell? What's happening? What is this?}

Qing looked at her palm in awe.

\textit{How do I even describe this?}

Flesh was crushed, bursting and trickling down, as the sensation tickled her fingers almost as if chattering to her.

\textit{Right in this very hand...}

The feeling of bones breaking and shattering still lingered vividly.

"Haeuhahhh..."

Qing exhaled a thrilled sigh.

The Elders turned pale at the sight.

"T-This crazy thing..."

\textit{Another terrifying Killing Star had ended up entering this place!}

The Elders lamented inwardly.

However, since the Demonic Cult had so many madmen, they didn't wet themselves or vomit.

There were even some who enjoyed both cannibalism and necrophilia simultaneously, so a woman who enjoyed crushing people was honestly nothing.

However, teaching martial arts to such a bitch was another matter, naturally draining their faces of color.

Qing, savoring the aftertaste, looked at the Elders who were trying to sneak out.

\textit{Come to think of it, who are these aunties anyway?}

\textit{Why did they suddenly swarm and come at me?}

Whether they stayed or left didn't matter since Qing didn't know their names or identities.

However, she needed to at least finish hearing what they had to say.

"So, what did you mean by the Blissful Maiden Arts not being a Demonic Arts? One of you stay and explain."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Originally, Dual Cultivation was a Health Technique of Daoism.

It was a Qi Circulation method where two people (or more!) exchanged True Qi through intimate acts.

And also, it allowed for some pleasure at times.

Originally, it led to happiness for all, making it a Health Technique.

Therefore, techniques like Collect Yin Supplement Yang or Collect Yang Supplement Yin were not usually one-sided.

Both men and women cultivated, with men gaining Yin and women gaining Yang in return.

Thus, sects that primarily practiced Dual Cultivation and did not harm their partners lived well.

There was even a joke that the disciples of the Blossom Ascension Sect, the Greatest Red-Light District Under The Heavens, had such an immense income that they ate elixirs instead of food.

However, once a man entered the Bliss Palace, he never came out again.

Naturally, this earned them the enmity of the entire Wulin.

The Blissful Maiden Arts was a Secret Manual for Dual Cultivation, enhancing the dantian by circulating and harmonizing various energies within the body after intercourse.

The downside of typical Dual Cultivation was clear.

After all, collecting miscellaneous Qi couldn't lead to a high realm.

However, the Blissful Maiden Arts was an Inner Qi Cultivation Technique designed to overcome this flaw.

Therefore, only the Palace Leader could master it.

And through this, the Bliss Palace Leader could dominate the palace with unparalleled martial prowess.

Thus, the loss of the Blissful Maiden Arts was a significant shock to the Elders.

In any case, the Blissful Maiden Arts could be said to inherit the orthodox lineage of Daoism...

The one Elder who remained explained this and then fled.

Qing was satisfied with the explanation.

\textit{What the… Then I was allowed to master it, huh.}

Qing hesitated... and then invested her Practice Points.

Since the initiation felt like having her brain gnawed on, hesitation was inevitable.

Upon doing so, the Sutra forcibly permeated her mind.

As usual, the prelude began with the Imagery of who created it and what they saw-

\begin{quote}
\textit{People enjoy the path of mutual growth with pleasure, experiencing love as the pleasure of cloud and rain, flying and falling freely in the vast sky.}

\textit{But this Fairy was born as a Stone Maiden, cursed by the Heavens, never knowing joy, giving only sorrow to her husband, and seeing it as a lifelong regret.}

\textit{Thus, this Fairy created this Sutra of two hundred sixty nine characters to explore a new world.}

\textit{Through this, the creator, too, discovered the true pleasure of a woman, previously unknown in life...}
\end{quote}

Even amidst the horrific sensation of someone roughly kneading her brain, Qing felt something was off.

\textit{About this sutra… isn't there something… wrong with it…?}

The Administrative Elder, who had stayed behind due to weakness, did not mention the effects of the Blissful Maiden Arts.

After all, she wanted to leave as quickly as possible.

Moreover, since the question was why it wasn't considered Demonic Arts, there was no need to explain further.

But one must ask themselves; why was it specifically named the Blissful Maiden Arts?

Because it was a Dual Cultivation technique for women to enhance their pleasure, hence the name Blissful Maiden Arts.

Fundamentally, it had the qualities of Fairy Arts, elevating a woman's beauty.

Additionally, it greatly increased flexibility, enabling all sorts of extraordinary positions in Daoist practices.

It made one resilient to cold and heat, toughened the skin to avoid injuries, and prevented tanning, allowing uninterrupted outdoor activities.

Most importantly, it had this major function.

It significantly enhanced the pleasure a woman felt.

An extraordinary martial art created by the Stone Maiden and imbued with her lifelong regret.

So potent, in fact, that it could even cure a woman's frigidity.

\begin{lstlisting}
	The chapter title is a reference to Keigo Higashino's short story collection, 犯人のいない殺人の夜/ Murder Night Without a Culprit, published in 1990
\end{lstlisting}