\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (8)}

Madam Kang seemed displeased with Qing's fussiness.

Of course, Qing didn't really care what she thought.

"But why do I suddenly need to learn to play music?"

"Music? This madam said it was ceremonial music."

"Isn't that the same thing?"

"Do you call swordsmanship a mere act of 'playing with blades'? This madam will teach you the ceremonial music known as Heavenly Heart Harmony, so you must learn it quickly."

Madam Kang spoke sternly.

However, Qing was still indifferent.

"Me? Why?"

"Because you stole the Fushen-di, you wretched wench!"

"Stole? What do you mean stole? That's harsh. I didn't pull such dirty tricks. I just killed him and took it, you know?"

"To think that one could brag so boldly about robbery."

"Don't you know the law of the strong? The winner takes all. So. Fushen-di. Equals. Mine."

The effect of the words ‘law of the strong' was tremendous.

Madam Kang closed her mouth and trembled in frustration.

"...E-Euhhh!"

Qing grinned and asked.

"So, why do I have to learn ceremonial music now of all times?"

"You do not need to know."

"Then, I won't learn it either."

"Are you daring to defy the Supreme's order?!"

"I don't know. And I don't care. I never heard that kind of order. Tell him to come and explain it to me himself. Then I'll decide whether to learn or not. If he doesn't, then oh well."

Qing spoke as such before laying down completely.

"You wretched bitch!"

"Oho. Hey. Watch your mouth. I have a weapon right now."

Qing swung the Fushen-di while lying down.

The Fushen-di was a flute made of a single piece of Cold Iron.

It was refined from Ten Thousand Year Cold Iron and was as sturdy as a Divine Weapon.

In Jianghu, something as long and sturdy as the Fushen-di could be called a short staff.

A short staff was a very fascinating weapon, adaptable to any weapon arts that are held with hands.

Although the power it could output was, of course, much less, it could still be used in the stead of swords for swordsmanship, dao for dao techniques, or spears for spear techniques.

"E-Eeek…!"

Madam Kang was at a loss.

Yes, she was ordered to teach her, but was she supposed to, even at the cost of revealing the cult's secrets?

And even if she did, would a so-called virtuous expert of the Orthodox Factionf cooperate?

"I'm going to sleep, so close the door and leave, okay? It'll be better for you to listen while I'm being nice. My leg is just an inconvenience, not completely useless."

"Keuk."

"Aren't you leaving? I'm gonna sleep, okie? I'm falling asleep now, okay? Good night!"

Qing closed her eyes completely.

Even though the sleep that once been lost wouldn't return, the important thing was to convey her intent.

Qing's innate sense of tact, honed by tiptoeing around the ‘line' countless times, screamed.

Right now, Qing had the high ground.

And that this dormitory supervisor-like teacher had no choice but to teach her by any possible means.

Qing's ability to read the room and find the most advantageous situation for her had practically reached the heavens.

Honestly, wasn't her current peaceful coexistence with the Demonic Cult proof enough of this?

She had only made one mistake with the childish menace that was the Alleged Supreme, who had anger management issues.

But even then, hadn't she laid low and crawled afterward?

Qing's sharp instincts were not wrong.

Madam Kang was seriously conflicted.

Did she have to report to the Supreme?

However, Madam Kang was someone who had known the Supreme for a long time.

If she tattled that ‘the wench refuses to learn,' the Supreme would likely blow her head off, saying she was meaninglessly boasting about her own incompetence.

Once a command was given, it had to be executed by any means necessary.

That was the Supreme's strict order.

"...Fine. If you swear on your sect and your master to learn the Heavenly Heart Harmony if I tell you why, I will explain."

"Um..."

Still, it felt kinda shitty to swear on the Divine Maiden Sect and her master.

\textit{Ah, so this is why they always make you swear on your sect and master, huh.}

\textit{But you know… She didn't say anything about how I had to learn diligently, right?}

It was a cunning thought more typical of a Demonic Adept.

"Alright. I promise."

Qing nodded.

Madam Kang, who thought Qing was a Female Expert of the Orthodox Faction, believed her without any doubts in mind.

And this was exactly why Sun Tzu had always emphasized so vehemently the importance of knowing both oneself and the enemy.

After all, all deceptions ultimately stemmed from this.

They had to know the enemy, but did not know that a scammer was a scammer.

They had to know themselves, but did not know that they were the ones being deceived.

"Haa. It was during the time when the Celestial Martial Emperor was alive..."

\textit{Again with the Celestial Martial Emperor?}

\textit{This old man is everywhere.}

The Celestial Martial Emperor didn't just mess with the Emperor.

The Emperor was rather let off lightly precisely because he was an Emperor.

After all, the most he did was shake him by the collar at the top of the Imperial Palace.

In the case of the Blood Cult, he broke the back of the Blood Maitreya.

He raided the main headquarters of the Forces of Evil, massacring the leaders and forcibly disbanding it, thus eliminating a future threat in Jianghu.

The Heavenly Demon Divine Cult was also one of the threats.

The Celestial Martial Emperor killed both the Heavenly Demon and the Minor Heavenly Demon and stole the Heavenly Demon Spirit from the Heavenly Demon Library.

"Heavenly Demon Spirit?"

"It is a treasure containing the Insights of the first Heavenly Demon Patriarch."

"It must be very important, huh?"

"That's..."

Madam Kang hesitated.

Was it right to reveal everything?

Qing pressured her.

"Don't hold back, explain in detail. If you hide anything, there will be no ceremonial music or whatever."

But revealing the secret was less terrifying than Qing not learning the ceremonial music.

Because if she didn't learn, her future beyond that was bleak.

Such rigid internal culture without forgiveness for failure was harmful.

After all, human nature dictates that personal minor losses feel more painful than the organization's massive losses.

Except, Qing, out of all people, had no right to mock the Heavenly Demon Divine Cult's current state.

In her homeland, the great Republic of Korea, an absolute majority of companies operated like this.

"About twenty years ago, the Divine Cult's espionage unit discovered the hidden records of the Celestial Martial Emperor."

The Celestial Martial Emperor couldn't bring himself to destroy the Heavenly Demon Spirit.

It was the essence of the outer martial arts lineage rooted in the Zoroastrian tradition, similar to Buddhism or Daoism.

Though it belonged to the Demonic Cult, as a martial artist, even the Celestial Martial Emperor couldn't destroy such a profound essence.

Instead, he hid it so well that no one could find it.

And the Divine Cult, mobilizing all its resources, discovered the location where the Heavenly Demon Spirit was hidden and named it the Heavenly Demon Tomb...

"Heavenly Demon Tomb?"

"It's a secret cave that sealed the Divine Relic containing the Spirit of the Heavenly Demon Patriarch. What else would you call it?"

Qing thought.

\textit{The name makes it sound like there's a well-flying horse buried there.}

The entrance to the Heavenly Demon Tomb was sealed with a complex mechanism, which was found to be the work of the legendary blacksmith, Banchi.

To open the entrance, one had to play the favorite tune of Banchi's wife on the Fushen-di.

That tune was the Heavenly Heart Harmony.

Forcing it open would collapse the entire secret cave, burying whatever inside it forever, whether it was the Heavenly Demon Spirit or something else.

And for reference, the Divine Cult have been searching desperately for the Fushen-di.

Finally, the Fushen-di was found, but Qing had completely bamboozled it.

Qing looked coldly at the Fushen-di.

\textit{So this is why all this fuss was happening.}

\textit{Damn it. What a mess for picking this up.}

\textit{This doesn't even mean anything tor me. Just a lousy dogshit flute.}

If the Fushen-di could hear, it would be outraged.

After all, Qing had eagerly picked it up for its worth of ten thousand gold.

Qing shifted the blame once more.

\textit{What is wrong with that guy called the Celestial Martial Emperor?}

\textit{If he was going to hide it, he should have done a better job. Why was it handled so sloppily?}

Anyway, it was a promise made on her master's name.

She would have liked to say she doesn't make promises with bad people, but swearing on her master made her feel uneasy.

So Qing kept her promise.

However, her attitude was extremely poor, listening only half-heartedly.

"Now, the beginning melody should be mournful and soft. Look at the score there. In the measure following the first part, the breath should be as fragile as if it's about to break, like a faint, wheezing breath..."

Squeak, squeak.

Qing blew the flute loudly.

"What? No, what did I say? Don't blow like a wild horse. Produce a thin thread-like tone as if it's about to break..."

"Agh shit, madam, how about you try blowing the Fushen-di once? I'm putting in my all the Inner Energy I can and you expect a what? Thin sound?"

"No, it is not a matter of technique. It is the lack of intention! Ceremonial music is about occupying the space with the performer's Imagery!"

"The Imagery doesn't suit my taste, you see. Why don't we arrange it more excitingly? I doubt the Celestial Martial Emperor liked such breathless sounds either."

Qing had actually seen the Insights left by the Celestial Martial Emperor.

He was an old man who would gulp down liquor by the jug, definitely not someone who would favor the mournful sound of a flute.

Moreover, the music of this era felt extremely boring to Qing.

More than anything, it was slow and dragging.

"We have a long way to go. How can you produce a proper sound with Inner Energy at this rate? I didn't want to resort to this method, but..."

Although Madam Kang inherited the legacy of a shaman, the Supreme did not respect her.

As such, she was one of the few women who survived long under the rule of a tyrant.

That meant she had prepared herself accordingly.

"Soyeong."

At that, the maid standing behind her flinched.

She was the maid who had delivered the martial arts bundle to Qing.

"Since you seem so uninterested in the lesson, this girl will be punished for your mistakes."

"Ehhh?"

"Look closely and remember. That this girl is being punished because of you."

Madam Kang unbuckled her belt.

It seemed a bit unusual at first, but once it was in her hand, it revealed itself not as a belt but as a whip.

The maid trembled as she undressed, and then Smack!

A long scar appeared on the back of the girl, who seemed to be just twenty years old.

Madam Kang's hand was ruthless, splitting the skin and causing blood to ooze out.

Qing frowned.

"Ouch. That must hurt..."

At the same time, she thought.

\textit{A kid getting beaten?}

\textit{But wouldn't it be effective only if they were at least somewhat acquainted?}

It was a level of Evil Karma similar to Jian Buxi, so in the Demonic Cult, she was only a budding villain.

Even so, she was still in the triple-digits.

Watching one villain beat another of their own kind didn't particularly affect Qing.

\textit{Huh, she looks like she's pretty handy with the whip.}

\textit{Should I learn some whip techniques as well?}

Meanwhile, Qing was quite interested in a different way.

Because of that, Qing's attitude toward the lesson didn't improve.

Whip! Whip! Whip!

Thanks to this, the maid was slashed up so badly she couldn't endure it and fainted with her eyes rolled back.

Madam Kang glared at Qing with eyes full of malice.

"You heartless wench. How can you not feel any guilt seeing an innocent girl fall into such a state before your eyes!"

"What? Hey, that's kinda funny for you to say. I mean, you're the one who beat her up, so why are you taking it out on me? How is it my fault? How absurd."

Madam Kang finally glimpsed upon Qing's true nature.

She was an extremely ruthless wench.

But Madam Kang wasn't one to back down in terms of ruthlessness either.

"Ah, I see. Fine. If she is a stranger to you, let's change who gets punished. I heard there's a girl who attends to you at Bliss Palace?"

"...? There's such a person?"

Qing tilted her head.

"Do not pretend you do not know. I heard she rose quickly in rank because you favor her. If she gets punished instead, you might take the lessons more seriously."

\textit{What the fuck? Is she talking about Crutch No. 2?}

Qing sighed deeply.

\textit{I was lenient because she's such a boomer, but now she's pushing her luck.}

"Hey, Madam. Teacher? No, that ain't it. Professor!"

"Hmph. Now you call me that."

"Whatever. Anyway, if a student can't learn, it's not the student's fault. It's the professor's fault for not teaching well."

Qing got off the bed and stood up.

Upon seeing how she dragged one leg as she limped forward, it was an oddly chilling sight.

"Professors are all the same, huh. So clueless. They can't get their shit together. What does an undergraduate even know? They shouldn't be expected to know anything. If you bombard them from the first class, how can they possibly understand? So, you're a failure as a professor."

"Wha-what is this, why are you coming..."

"Be quiet!"

Smack!

Qing's Fushen-di cut through the air.

She wanted to deliver a nuclear noogie, but given her current pretense of limited mobility, it was somewhat unrealistic.

However, although the feel of the Fushen-di was not great, its attack range was superior to that of a nuclear noogie.

"Kyak! Heuk, Heu-heuk..."

Madam Kang, who fell in one blow, rubbed her crown like a madwoman.

After all, it felt like her head was on fire.

She was busy rubbing her head and looking at her palms, before rubbing her head again.

It felt like her scalp was torn and her skull was broken, but there was no blood in sight.

This was the precise distribution of force Qing had learned through her own beatings.

"What is this! H-How can a student h-hit a teacher so brutally..."

"Professor, don't move. If you act up, you'll die. If I swing this flute, your skull will be split in half, you see. Professor? Why are you trying to yap without knowing your place? Why are you trying to plant seeds that you cannot take responsibility for? Do you have to do the sowing? If you don't like it, you should have just let me retake the class. If you don't want to see my face again, you should have just graduated me quickly. Doesn't it kinda make you ashamed thinking that you have to see me next semester? Isn't it like a chain of resentment?"

Qing's eyes glinted fiercely.

Madam Kang couldn't begin to fathom what exactly her words meant and just trembled.

After all, she had only heard that Qing was a female from the Orthodox Faction, so she didn't think much of her. But in reality, the person before her was a maniac.

Qing bent deeply, putting her face as close to Madam Kang's as possible.

"Teacher."

Madam Kang's breath hitched.

How could a young girl exude such intimidation...

"Why, why are you..."

"From now on, if I make mistakes, misunderstand, or lose focus during lessons, it's all your fault, Professor, or rather, Teacher, right? Yes? You agree, right?"

"How does that make any sense..."

"What? What did you say? Let me reiterate. What happens if you do something wrong? You get punished. You get beaten the shit out of for failing to teach. Also, this is confiscated."

Qing naturally took Madam Kang's whip.

Then she smiled brightly and continued.

"Now then, Teacher. Let's continue our lesson, shall we?"