\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (6)}

A new member of the fam joined Qing's dantian.

It was a newcomer that was cold and dark, with an Extreme Yin nature.

Heavenly Ice Demonic Qi!

It was an evil Demonic Qi from the Northern Sea.

The Heavenly Ice Demonic Qi entered the dantian triumphantly.

And then, it saw the Zhu Xiang True Qi.

The Zhu Xiang True Qi, a Divine Art of Orthodox Yang, looked at the newcomer once and sent a signal to the Bliss True Qi.

The True Qi of the Yue Maiden nodded once, pretending not to notice.

The Bliss True Qi got up and the Heavenly Ice Demonic Qi immediately turned around and ran away.

"This one can also be trained automatically. Fat stonks…"

Qing felt the Heavenly Ice Demonic Qi moving around on its own inside her body.

The Heavenly Ice Sura Demonic Art had reached Three Stars.

She had tested it last night, and its effectiveness at Three Stars was just enough to offset the First Star of the Blissful Maiden Arts.

Since the stat boost from Golden Martial Arts was higher than Red Martial Arts, just the Heavenly Ice Sura Demonic Arts alone was far from enough to counteract the side effects of the Blissful Maiden Arts.

\textit{What should I do?}

\textit{Do I have to learn the Snow White Divine Arts?}

In fact, Qing had originally thought of exchanging 1500 Points for a certain martial art.

It was an Inner Qi Cultivation Technique called the Yijin Cleansing Method\footnote{易筋经/ Yijinjing, lit. 'change tendon method'. It's a real book, although obviously it won't make its practicians jump over buildings}.

She heard about it once in a conversation with Ximen Surin.

'Master, if I could learn just one martial art in the world, what would be the best?'

'That would be the Yijin Cleansing Method.'

'Yijin Cleansing Method?'

'Yes. It is the best Inner Qi Cultivation Technique for someone walking the righteous path. Its effect of protecting the mind from inner demons is second only to the Zhu Xiang's Heart Cleanse Mirror, and in terms of strengthening the dantian and meridians, there is no martial art in the world that can compare to it.'

'Then, compared to Zhu Xiang's Heart Cleanse Mirror, which one is- AHHK!! It hurts, Master…'

'My disciple is truly asking for a beating. Tsk. The Yijin Cleansing Method is the greatest martial art of Buddhism. How can you even begin to compare it with our Daoism, which follows a different path? If only you could learn it, haaa. Enough. Forget it. Talking about something you cannot obtain will only leave regrets, so do not bring it up again in the future, Disciple.'

'Alright…'

And it had gone something like that.

So, she searched for it in the Martial Arts Window, and it turned out to be Purple.

It was truly an irreverent thought, but there was no doubt it was a better martial art than Zhu Xiang's Heart Cleanse Mirror.

After all, if the two were actually comparable, Master wouldn't have thrown a nuclear noogie with such displeasure.

It was precisely because she had nothing else to say that she reacted that way…

\textit{So, if I went back and said, 'Ta-da! Your disciple mastered the Yijin Cleansing Method!' How happy would she be?}

\textit{At least, that was the plan.}

\textit{But in the end, I've only increased the number of my Demonic Arts…}

\textit{But I needed to get stronger right away. What else could I have done?}

After all, Qing wasn't blind; she could clearly see the crowd of Masters towards the end of the kidnapping procession.

Qing was a Master beyond her experience, but in the Heavenly Demon Divine Cult, she was just a common Peak Realm martial artist.

\textit{After all, the fact that they're leaving me alone even at this moment is because they see me as weak.}

\textit{Sure, I was pretending to be a cripple, but they must be confident that I can't escape, even if they let me try.}

\textit{So let's collect as many martial arts as possible for now.}

\textit{Just like when I reached the Peak Realm, if my realm somehow increases, I'll also aim for the Alleged Supreme,}

\textit{And if I don't reach it?}

\textit{Well, I guess I can just continue accumulating my strength, keep an eye out, then cause a shitfest before running away?}

\textit{I underestimated him because that motherfucker of a leader was absolutely schizo and delusional, but in reality… It was a tiger's den.}

\textit{But what could I have done there anyway?}

\textit{How could I have known I'd be kidnapped in the front yard of my own home?}

\textit{Honestly, that was too fucking much. Motherfucker was out to get me.}

Rumble.

A growl interrupted Qing's thoughts.

"Ah. I'm hungry."

The sun was already high in the sky.

Having taken a night walk without sleep, she had skipped breakfast and slept until now.

\textit{Didn't someone wake me in the morning, though?}

\textit{Was it a dream? Mmm. I dunno. I'm hungry.}

\textit{Is it not lunchtime yet?}

\textit{No way, could I have missed it?}

Right as Qing was licking her lips with a hungry stomach, she heard sounds from the other side of the wall.

-Kyak, kkeuahk, euk, ahk, kyak.

It was coming from the next room.

To be more precise, it was Jian Buxi's room.

What's going on now?

Is that idiot getting beaten again?

Qing frowned and got up.

Even then, she didn't forget to limp while dragging her foot and opened the door to the next room.

Just as expected.

A scene of harsh bullying was unfolding.

However, it was slightly different from what Qing had expected-

"Oh, Junior Sister! You're awake!?"

Jian Buxi, who was sitting on five piled-up disciples, waved cheerfully.

The disciple at the bottom looked especially pale.

She's going to suffocate at this rate, yeah? What a pity.

"Excuse me? Miss Jian? What are you doing right n-"

"Eung? Discipline and education! I'm a Second-Grade disciple now, after all! I have a duty to educate the Junior Sisters!"

\textit{I guess she did mention something like that yesterday.}

\textit{Ah, so she was actually serious about it, huh.}

"Oh dear, Junior Sister Cheon? Why are you not bowing properly? Plant your head firmly. How are you going to live in this harsh world if you're so weak? If it's too hard, should I just end it for you? So that you don't need to live in this harsh world?"

Junior Sister Cheon, startled, fumbled on the floor.

She found a fallen liquor cup and planted her head on it.

For reference, a liquor cup in Zhongyuan could only hold two spoonfuls of alcohol. Basically, it was tiny.

Wow, isn't this at the level of planting your head on a bottle cap?

Honestly, it was a miracle that transcended time and space.

It basically meant that, anthropologically speaking, people's thoughts are the same now as they were then.

Especially when it comes to tormenting people.

The philosophers who argued that human nature is evil might have been right, after all.

Right as Qing was watching with fascinated eyes…

"Eup, urgh…! Blegh!"

This time, a woman next to her vomited.

"Junior Sister Dab? I specially prepared raw meat for you because cooked food is harmful to the body. Since you love food so much and hate seeing it wasted, shouldn't you set an example?"

"But…"

"You know what to do, right?"

Junior Sister Daap looked at the floor with trembling eyes.

\textit{Ah. So she's the one, huh.}

\textit{The one who makes people eat raw meat and then makes them lap it up if they vomit it out.}

\textit{Now that I look at it, this just turned out to be Jian Buxi's revenge.}

\textit{Then, I should let her enjoy it-}

Jian Buxi looked pleased.

And right above her, her rising Evil Karma was, Oing?

Jian Buxi's Evil Karma rose right before Qing's eyes.

From -149 to -150.

\textit{That's weird?}

\textit{I definitely dropped it to -145 yesterday, didn't I?}

\textit{Why is it back to 150 again?}

It was at that moment.

The woman named Cheon, who was trembling with her head planted, lost her balance and fell with a thud.

The round, dark bruise on her forehead made Qing burst into laughter.

"Junior Sister Cheon? Are you okay? With that, that's five times, right?"

"Pant, n-no, it is not."

"Lying is not allowed. You're a bad girl."

Jian Buxi pulled out and threw a binyeo.

Even though her movements were clumsy, she had quite a knack for it.

The binyeo stuck into Junior Sister Cheon's thigh with a Prick.

"KYAAAK!"

"Huh? Ehhh? Are you letting out a sound? Are you allowed to make a sound when your Senior Sister personally educates you? Yes or no?"

"I-I apologi…"

"It's because you're not tense enough. Didn't Junior Sister Cheon teach us this yourself? That a beating would help us tense up?"

Jian Buxi grabbed the woman called Cheon's hair and swiftly kicked her.

She kicked her firmly, making extra sure she couldn't run away.

Meanwhile, Junior Sister Cheon cried and begged for forgiveness.

"I-I'm, I'm sorry, I'm sorry, I'm so sorry…"

"Is saying sorry enough? Ah. Right. Junior Sister Cheon always said that, didn't you? Whether being sorry is enough. By the way, if being sorry isn't enough, then what even is the point of it?"

"I was wrong…, Sob…"

"Junior Sister Cheon. Didn't your Senior Sister just ask a question? Is the Bliss Palace a joke to you? Do I look like a fucki- No, I mean, do I look like an intercoursing joke to you?"

"I-I was wrong! Senior Sister! Please forgive me!"

Junior Sister Cheon groveled and begged, plastering herself onto the floor like some bug.

Right as she did so, Jian Buxi's Evil Karma dropped.

-149.

Qing's eyes sparkled.

\textit{This time it dropped? What's different about it?}

\textit{Why does it go up and down when she's enjoying the same thi…}

\textit{Eh? Is it that?}

A thought suddenly came to Qing.

She pointed at one of the women.

"Senior Sister, Senior Sister. That one's glaring at you weirdly."

"What!? How exactly is she glaring?"

"Look, look. She's giving you a rude look right now. Isn't she treating you far too lightly, Senior? How can she just shoot those dirty looks at you? Couldn't it be that she's looking down on Senior Sister?"

"N-No, I am not! I didn't do that!"

"Junior Sister Jin. You liked to draw, didn't you?"

"Hieeek…!"

"Junior Sister Jin? You should strip, yes?"

Jian Buxi spoke while drawing a dagger.

\textit{Ah. So that's what she meant by drawing, huh?}

Qing understood instantly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The revenge spree ended.

It seemed that tampering thoughtlessly with an evil person only made them more vehement and increased their Evil Karma.

Perhaps it's because it turns a bad person into a worse one?

It seemed to be judged that way.

In the same sense, breaking and crushing the heart and mind of an evil person could be considered as accumulating Righteous Karma.

Then, perhaps the condition for Righteous Karma was to prevent future evil deeds.

\textit{Come to think of it, even when it came to Changming'er, that Mission Window motherfucker ha-...}

\textit{Ah, but the kiddo must be living comfortably, right?}

\textit{Even though I am suffering like this…}

\textit{Why?}

\textit{Why only me?}

\textit{Now that I think about it, this is kinda fucked, isn't it? It's pissing me off.}

This flow of consciousness and thoughts Qing had enraged her.

Half of the Bliss Palace disciples were lying down with dead eyes, taking the minimal number of breaths needed to continue surviving; the rest still had a lively glint in their eyes.

\textit{Shit, I'm getting all heated too. Let's play around with just one of them.}

\textit{Which one should I choose\~{}?}

Right as Qing was selecting a target to vent her anger…

Jian Buxi suddenly hugged Qing.

It was a pretty comfortable ride, or rather a comfortable villain's embrace.

She seemed to have gotten quite used to her calling, her duty, to be a crutch.

The crutch spoke to Qing.

"Junior Sister! You're hungry, right!? Let's go eat lunch!"

\textit{Lunch!}

Qing's killing intent immediately subsided.

Why? Because food was an important, serious matter.

At least for Qing, it was.

\textit{But didn't Crutch No. 2 prefer something else?}

Curious, Qing asked.

"Senior Sister, this time, the uh… finishing touches? You're not going to do it?"

"Eh? Of course not. I'm the Senior Sister, right? I can't do that."

\textit{What does being a Senior Sister have to do with finishing them off?}

Qing asked again.

"You're a Senior Sister, though. So why not?"

"Challenges are for the Juniors to make. While Seniors can educate Juniors in exchange."

"Ah. So that's how the rules work, huh."

\textit{Well, I guess it makes sense.}

\textit{Imagine if being a Senior means you can just devour Juniors to your heart's content.}

\textit{Eventually, only the highest-ranked person would remain.}

\textit{They must have made that rule to prevent that.}

\textit{By the way, how the fuck can this be called a sect when it's like this?}

\textit{At this point, it's just a broken, dysfunctional group.}

Qing suddenly missed the Divine Maiden Sect very much.

And not long after, she would miss it even more.

Because today's lunch was a mess.