\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (3)}

And then, about an hour had passed.

The malefactor, who had been lying on the ground void of her hands, was now completely limp.

Jian Buxi wiped the sweat from her forehead with her sleeve.

After finishing, Jian Buxi's face was glowing with a radiant shine.

She put the nameplate, which had belonged to her Senior Sister just prior, into her pocket with a bright and innocent expression.

She was smiling brightly with a cheerful laugh.

Jian Buxi hugged Qing tightly and cheerfully walked down the corridor.

"Thanks to you, I had a real feast after a long time. Ah! Oh my! Did I introduce myself? I am Jian Buxi. And you are, Junior Sister?"

"Huh? Oing? I'm not your Junior Sister, though."

"…? Are you not Junior Sister Ximen Qing?"

"Yes, my name is Ximen Qing, but…?"

"But you're not my Junior Sister…?"

"Why would I be your Junior Sister…?"

They stared at each other blankly.

Qing thought to herself.

\textit{-149. One hundred and fifty has become within the one hundred and forties?}

\textit{And it doesn't mean like my Righteous Karma increased or something.}

\textit{Is it because I was half into killing her and she finished her off?}

\textit{Come to think of it, even villains could accumulate Righteous Karma by slaying other malefactors.}

\textit{But does that make a villain a good person?}

\textit{If someone did bad deeds, wouldn't divine punishment still need to be delivered?}

\textit{But she didn't seem like a bad person either.}

\textit{Does that even make sense, though? She's jacking off evil people when she's not even a bad person? What?}

It was quite the conundrum.

\textit{Can bad deeds be offset by good deeds?}

\textit{Then, were there villains who shouldn't be treated as human, even though they had accumulated righteous deeds?}

\textit{But how the hell am I supposed to know that?}

So, what did she do about this conundrum? Qing stopped thinking about it.

After all, there were plenty of other villains to deal with that were blatantly evil.

There was no need to worry about reformed villains.

"I am fairly sure I heard that Junior Sister joined the Bliss Palace yesterday, though?"

Qing spoke in a serious manner, without a hint of jest.

"What are you talking about? Who do you think my Master is that I would join the Demonic Cult? That's practically blasphemy."

"Junior Sister's Master? Who is it?"

"She is surnamed Ximen, with Su and Rin as her given name. Ximen Surin."

"…? Did we have such an elder in the palace?"

Qing was taken aback.

\textit{The fuck? If she was a part of this palace, why would Master even be at the Divine Maiden Sect?}

"Of course not. How does that make any sense?"

"……?"

Jian Buxi looked utterly confused.

However, Qing had a rough understanding.

Didn't that so-called Alleged Supreme say something like that?

He said to treat Ximen Qing well in the Bliss Palace and not to spare any martial arts or elixirs.

\textit{That expressionless and idiotic brat probably misunderstood the meaning and caused this mess.}

\textit{Well, I should play along for now.}

\textit{I need to secure the martial arts and elixirs, after all.}

"Alright. Whatever. No biggie. I'll try being a Junior Sister."

"As expected! Junior Sister Xi. You can call me Senior Sister Jian."

\textit{No way! To think she would change someone else's surname so casually!}

\textit{How could this bitch be so ignorant that she doesn't even know the Ximen surname\footnote{Chapter 25}?!}

Qing was appalled by her ignorance.

She kept thinking that the girl was a bit lacking in the head.

\textit{Still, the girl was somewhat kind…or maybe not.}

\textit{Wait, she's lacking in the head and not kind either?}

Qing drastically lowered her evaluation of Jian Buxi.

\textit{Senior Sister, you suit being my crutches better than being a Senior Sister.}

Qing decided to regard her as Crutch No. 2.

\textit{By the way, where did Crutch No. 1 go? That Gramps?}

It seemed there were many things to ask.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

To be honest, Qing couldn't understand why Demonic Arts were shunned.

Her Master said that all Demonic Arts inherently evoke an evil nature.

Hence, even though there are brutal martial arts used by the Orthodox Faction that remain as ultimate techniques, there are also techniques that are considered Demonic Arts despite not being particularly brutal.

But from the perspective of Qing, who had already mastered various Demonic Arts under the renowned White Hand Demonic Arts, well...

It was true that White Hand Demonic Arts and Black Slaying Demonic Arts had a uniquely satisfying feel.

It was also true that seeing a villain made her want to tear into their flesh with her fingers, beat them with long-ranged strikes, and crush their bones.

\textit{But even without that, wasn't killing villains a delightful and virtuous hobby?}

\textit{If I'm going to kill them anyway, what's wrong with playing with them a bit?}

\textit{It would be fun, and the villain would thoroughly regret their sins, right?}

Yet that makes someone evil?

What exactly made one evil anyway?

Honestly, in terms of side effects, even the Blissful Maiden Arts, a supposedly Daoist orthodox cultivation technique, had far more serious issues.

\textit{Ahh, it's actually a bigger problem if it feels too good, huh?}

Luckily, Qing had a suitable crutch supporting her, or else she might have ended up rolling around on the ground in an actual battle.

\textit{Huh, maybe I can kinda get used to this.}

Qing recalled that moment.

\textit{Hehe, it was nice...}

Qing inadvertently smiled with a subtle expression and then snapped back to her senses.

The problem was the uncontrollable nature of Blissful Maiden Arts.

Why in the world did it cultivate automatically?

Even now, she couldn't put a leash on it and it roamed around autonomously, expanding its influence at all times.

In fact, even the supposedly quiet Purple Lightning Demonic Arts joined in the chaos.

To be precise, the Purple Lightning Demonic Arts would first rush out from the dantian and run through the pressure points, with the Blissful Maiden Arts following closely behind.

As a result, both cultivation techniques were rapidly increasing her Practice Points automatically. But.

Originally, Inner Qi Cultivation Techniques were methods to absorb and refine True Qi.

By accumulating Inner Qi according to the Sutra, one could endlessly fill the dantian as long as their lifespan allowed.

Basic Arts formed the dantian and Fine Meridians.

When one became a formal disciple, they were taught advanced techniques to circulate and cultivate True Qi.

And then, when one reached a certain level, such as a First-Grade disciple or a named disciple of an Elder, they would then learn the secret high-level cultivation techniques preserved by the sect.

This way, the True Qi cultivated with lower-level techniques would naturally integrate into the high-level ones.

Alternatively, instead of absorption, the different True Qi could coexist in a symbiotic manner, flowing separately without clashing.

But Qing was different.

Her state was one where a Status Window and a martial arts genre was weirdly mixed.

She gained Practice Points by circulating True Qi, leading to advancements.

With each increase in stage, the corresponding abilities of the martial arts increased, and for cultivation techniques, the maximum Inner Qi also increased.

Reaching the Grand Star level resulted in significant gains, but that was it.

Qing, knowing she was different, would get frustrated every time she looked at her Status Window.

It seemed to mock her as if saying she was an outsider in this world.

Nevertheless.

The Blissful Maiden Arts were not the Essence Absorption Demonic Arts.

It was a cultivation technique that purified and refined the absorbed True Qi into pure Inner Qi.

It was indeed a legitimate Divine Art of Daoism.

If True Qi were to be put in anthropomorphic terms, it would look like this.

Blissful Maiden Arts regarded other Daoist True Qi as friendly companions, thus sharing the same dantian.

But Purple Lightning Demonic Qi was not.

As such, it felt compelled to purify this vile demonic energy into something pure and kind.

Thus, the Purple Lightning Demonic Qi, already in a pitiful state, was driven to the brink of an existential crisis.

Purple Lightning Demonic Qi fled the dantian.

And the Blissful Maiden True Qi chased after it.

Meanwhile, the Yue Maiden True Qi clapped and encouraged it on the sidelines.

The Yue Maiden True Qi, being a staunch separatist, would separate them if it felt the Purple Lightning Demonic Qi was in danger.

However, being fundamentally Daoist, it didn't stop the Blissful Maiden True Qi from tormenting its kin.

And the result of that was automatic cultivation.

Of course, Qing couldn't know these reasons.

However, the sense of crisis she felt was, at least, real.

An excess in anything was problematic.

Except for Inner Qi, of course.

Even feeling good had its limits.

Being unable to control your body was a big problem.

The side effects of just the One Star in Blissful Maiden Arts were this severe.

If her achievements advanced further, she might literally pass out every time she got hit.

So Qing thought.

\textit{There are martial arts that make one sensitive, huh?}

\textit{Then, could there be martial arts that make one numb?}

Fortunately, there was someone to ask.

It was the foul-mouthed old man who came looking for lunch, Crutch No. 1.

\textit{But why does this old man like me anyway?}

\textit{His karma is entirely that of a Great Demonic Adept, so it's kinda burdensome…}

"Grandfather, are there any martial arts that make a person numb?"

"They do exist."

"Oooh. There's really nothing you don't know. huh. So, what are they?"

"Tsk. Learning those will make you dull and inhuman. How do you not know that? You are only interested in such wicked things, you wretched girl."

"Who asked about that? So, what are they?"

"Damn girl, even when I worry about you, you give me shit for it."

"Who asked for you to worry about me? Who cares."

"Tsk. Ice Arts are usually like that, are they not?"

"Ice Arts?"

"You ignorant girl."

"Geez. Yeah, I'm ignorant. So, I'm asking you to help me out. Why are you yapping so much?"

"Tsk."

Cui Liweng clicked his tongue but still explained.

There were martial arts that quite purely interpreted the principles of Yin and Yang.

Yin is cold. Yang is hot.

Thus, Ice Arts was meant for freezing attacks.

And Flame Arts was meant for fire-based attacks.

Of course, the efficiency was disastrously poor.

If Ice Arts and Flame Arts were strong, every warrior in Zhongyuans would have decided their future based on fire or ice attributes.

Even so, Flame Arts were much better.

Comparing the two, the efficiency difference was such that it was embarrassing to even compare Ice Arts to Flame Arts.

Hot things burn instantly, but cold things could simply be pulled away, saying ‘Uht, it's cold'.

Why else would those ice masters of the North Sea Ice Palace be stuck in that cold land?

It was because Ice Arts were only useful in the North Sea.

It was a land already in extreme cold.

Only in cold weather did making it even colder have any noticeable effect.

Thus, even if an Ice Palace Master descended to Zhongyuans, they were treated as mere walking ice factories.

Still, they were not poorly treated because they saved on the expensive saltpeter used to make ice.

At this point, Qing's eyes lit up.

"Ah, then if I learn it, can I make chilled Longjing tea?"

"Bah!!! Chilled Longjing tea? What kind of crazy nonsense is that? Are you out of your mind?"

"Can't a person just want some chilled Longjing tea?"

"Dear child… Please, come to your senses. Stop this, okay? This old man is entirely at fault. Alright? So please, stop."

Cui Liweng looked at her as if she were the most pitiful creature in the world.

\textit{Hmm. Is it that serious?}

\textit{No, but like… Why?}

\textit{Why couldn't these primitive original cultivators understand the joy of chilled tea?}

There was cold tea in Zhongyuans, but it was usually sweetened with squeezed fruits or made from barley, rice, or corn.

However, fruit or grain teas were considered just beverages, even though they were called tea.

Real tea was strictly defined as the result of steaming, roasting, or drying tea leaves and brewing them in hot water.

"I'm perfectly fine, though. So, what's the strongest Ice Arts?"

"That would be the Supreme Yin Jade Maiden Divine Art."

Cui Liweng answered without hesitation.

In fact, it was something no martial artist was ignorant of.

"Supreme Yin Jade Maiden Divine Art?"

"Goodness, even a seven-year-old knows that."

"Stop calling me ignorant. I'm not going to tolerate it anymore. I'll end you."

Qing said that while managing her Martial Arts Window.

Supreme Yin Jade Maiden Divine Palm, Supreme Yin Jade Maiden Divine Cultivation, Supreme Yin Jade Maiden Divine Sword.

Three Purple Martial Arts appeared at the top.

It was the downside of Purple Martial Arts.

They were always split into several parts, making it impossible to obtain them all through Righteous Karma exchanges.

\textit{But if it's just Supreme Yin Jade Maiden Divine Arts, hmm…}

\textit{Isn't it a bit of a waste?}

According to Crutch No. 1's explanation, it's just a Purple Border in name… All it really does is add a refrigeration function, no?

But this is an emergency, to be fair.

\textit{I need to do something about the side effects of the Blissful Maiden Arts…}

Right as Qing was contemplating...

"What about it, you brat. Do you suddenly want to learn Ice Arts?"

"Why? Do you know any Ice Arts?"

"Seol Ganom mastered the Heavenly Ice Sura Demonic Arts."

What? A Demonic Art? Again?

Qing looked at her still-open Martial Arts Window.

Heavenly Ice Sura Demonic Arts. It was a mere Red Border.

The name seemed to imply it was one of the Greatest Demonic Arts Under Heaven or some shit, but it was only red?

\textit{The grade seems rather low…}

Well, to be fair, that's not the problem right now.

"If I learn that, will my senses become a bit numb?"

"It is not just at the level of numb. Ha. Forget it. Heed me, you brat. You'll become a tree trunk, a piece of wood. There's a reason it's called a Demonic Art."

\textit{Then it's perfect!}

\textit{And since it's a Demonic Art, the person who mastered it must be a Demonic Human, right?}

Qing's eyes sparkled as she asked.

"So, where does that Seol Ganom person lived?"