\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (2)}

The elders of the Bliss Palace saw nothing but unpleasant sights after barging in.

After all, two of their fellow comrades had been rendered utterly useless.

The Discipline Elder's dantian was damaged, turning her into an old woman, and the Inner Arts she had accumulated through unorthodox methods quickly leaked out as True Qi.

Meanwhile, the Training Elder's hands had become crippled.

They managed to retrieve her severed hands, but they were too damaged to be reattached.

In fact, a First-Grade disciple of the Bliss Palace was shocked at such a sight when checking on her teacher's bed.

So shocked, in fact, that she subdued her teacher and absorbed all her Inner Qi.

And the disciple thought that since she was the one to deal with the Training Elder, revealing this fact could make her the next Training Elder.

However, a young and inexperienced disciple rising to the position of elder would only make them a stepping stone for someone else.

As such, it was time to consolidate their newly acquired power.

Similarly, a ninth-ranked enforcer of the Discipline Hall forcibly transferred her crippled master's True Qi upon finding her.

The position of Discipline Elder was reserved for the highest-ranking expert and the ninth-ranked enforcer knew it was too much for her.

Thus, she, too, decided to consolidate her power quietly.

As a result, two bodies without a single culprit of their murders emerged that night.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Jian Buxi \footnote{堅布喜 lit. 'hard cloth happy'. Gyeon Pohee (견포희) in the original text}, the youngest Third-Grade disciple, led a rather difficult life.

She was constantly being beaten and used as an outlet for venting anger and the man she had barely managed to win over was taken from her. She couldn't even remember the last time she enjoyed a man's company.

Consequently, her martial arts skills didn't progress, though she excelled at various household chores.

Such a Jian Buxi received good news.

A new youngest disciple had joined.

She could finally be free from chores!

However, her joy was short-lived.

The newcomer was crippled! Her legs were completely disabled!

As such, Jian Buxi steeled herself.

The long-awaited youngest disciple turned out to be crippled?

\textit{Ha. If they think they'll get special treatment, they're sorely mistaken.}

\textit{I'll show my dignity as a Senior Sister!}

Jian Buxi kicked open Qing's door.

Despite being the first time doing this, she was quite a natural at it, having experienced it often herself from her seniors.

"Hey! Kid! What are you doing when the sun is so high in the sky?"

Qing squinted, looking for the window.

"Heh, oing... the sun isn't up, though..."

"What? How dare you not get up?! You lazy bum!"

Jian Buxi shouted loudly.

Qing slowly got up.

After all, the pitch of her voice was too high to pretend not to hear.

"Who are you?"

"What? Where are your clothes?! Why are you buck-naked!?"

Qing quickly covered herself with the blanket.

"Because this is more comfortable..."

"Get dressed and get up! Are you planning to slack off on your first day!?"

"Ah. Can you step out for a moment then? It's a bit uncomfortable with someone here…"

"Didn't you hear me!? I said you're late! Do you want to skip breakfast!?"

"Uht. Is it already time for breakfast? Does this place eat this early? Could you pass me the clothes next to you?"

"Get it yourself! Do you not have hands or feet!?"

"I mean, if I had to say, I guess I don't have my feet?"

Jian Buxi paused.

"Hmph. Hm. Fine. Just this once. After all, none of the Senior Sisters will be lenient with you just because you're cripp- I mean, disabled."

Qing watched the girl grumbling as she picked up clothes scattered around.

-151.

\textit{Is there no one normal in this place?}

\textit{Even the servants are fucking evil.}

However, breakfast was the most important priority.

Though she found it disappointing not to start the day with a refreshing bloodshed.

Qing picked up her clothes from under the blanket.

Then she boldly raised her arms.

"Alright. Let's go. To eat."

"What the- Why are you suddenly raising your arms?"

"Well, I mean. It's obviously because you have to take me?"

Basically, she was asking to be carried.

Her act of being crippled had improved to the point where she was deeply immersed in it.

In modern terms, she was consumed by her own method acting.

Her skill in deceiving two Unrestrained, many Transcendent, and countless Peak martial artists stemmed from here.

Qing classified people into three genders.

Men. Women. And evil people.

Starting from those with Evil Karma in the three-digits, gender was irrelevant.

Qing originally avoided direct contact with those she wasn't hostile towards.

Touching a man with bare skin was shameful if one was a man.

And touching a woman was somewhat pleasing but felt like a despicable ploy by using her current appearance.

After confirming her Evil Karma, Jian Buxi was no longer considered a woman, so Qing had no qualms about being carried by her.

"Hah, this nutc- No, I mean, this mentally il- No, sorry, I keep saying harsh things. Maybe it's because I've been hearing them all this time. Kid, are you perhaps a bit dim-witted? What exactly are you trying to do?"

"Why? What's wrong?"

Qing tilted her head.

Once again, it had returned. That expression.

The expression that clearly said, ‘Qing knows nothing'.

"Hah. Forget it! We're short on time! We need to hurry!"

Jian Buxi picked up Qing.

Qing was taller and larger than her Senior Sisters, thus making her heavier.

However, she fit comfortably into such a position, as if it was rather familiar.

In fact, it made it easier to carry her compared to when Jian Buxi had to serve as a human chair for her Senior Sisters.

As they moved towards the dining hall, Jian Buxi encountered Yoo Nangryang, the fourth-ranked Third-Grade Disciple and a Taskmaster of one of the four factions of the Second-Grade disciples.

Jian Buxi immediately shouted.

"Senior Sister! Did you sleep well last night!?"

"Yes, yes. Did you sleep well too, Junior Sister?"

"Yes! Thank you!"

Qing frowned.

\textit{Why is she shouting so loudly in the morning?}

\textit{She must be a bottom-feeder out of the servants. Should I switch her out?}

Qing looked at the other servant.

Her Evil Karma was just over two hundred.

\textit{Well, a hundred and fifty was still better than two hundred.}

As such, Qing just sighed deeply and decided to let it be.

"Heh? What did I just hear? What was that sound?"

"Uht, u-uhm…"

"What's this? Why are you carrying her? Oh, is she that cripple who just joined? Wowwww, look at how nice the world has gotten. How can a cripple comfortably lie in a Senior Sister's arms like that? Did she think you were an easy mark or something?"

"Well, her legs are…"

"Hah! What a retarded bitch. The both of you, that is. In my opinion, a Senior Sister who can't properly train a junior is much more of a retarded bitch than the junior who doesn't know her place. I'll teach you what proper training is, so remember it well."

Yoo Nangryang sneered and raised her hand.

The slap, containing a move from the Twelve Palm Techniques of the Bliss Palace, flew towards Jian Buxi's face.

Jian Buxi buried her face between her shoulders.

However, the slap was blocked midway.

It was because a black hand grabbed her wrist tightly.

For reference, Qing was on her way to the ever so important event known as breakfast.

As such, there was no way she wouldn't be displeased with the interruption.

Qing smiled with a face as white as a ghost as she spoke.

The first character in the White Hand Demonic Arts was, in fact, 'white'.

And since white originally had a connection to wickedness...

"Hello, excuse me. Do you know what you call someone with no hands in just one word?"

"Haaa? What kind of bullshit are you…"

"Wrong! Bullshit is not the right answer. The correct answer is ‘you'."

It was a repeat of yesterday's scene.

A hand void of its original support fell off, causing a loud scream to erupt.

And the delightful sensation of crushing flesh and bone, even though she experienced it yesterday, was… Eh?

\textit{Huh... huh...? This feeling, e-eut. It feels... too, too…}

\textit{Ah. It feels too… good…!}

"Uhk."

Qing let out a breathless moan.

Jian Buxi, who was holding her, snapped back to her senses.

She had briefly lost her mind due to the recent events.

She found Qing trembling in her arms, thus bringing her back to reality.

\textit{What's wrong with her?! This is epilepsy, right?! She's having a seizure here?!}

\textit{What should I do?! S-Should I take her to the Medicine Hall?}

\textit{B-But I need to take the u-utensils with me!}

Jian Buxi didn't know what to do and just hugged Qing tightly.

After all, she remembered seeing someone hug a person having a seizure in the village she had lived in before.

It seemed to work, as the youngest's seizure subsided.

"Hey!? Are you okay!? Are you coming to your senses!?"

"Huuu... Huuuuu... Huuuuuuuuuuu..."

Qing took deep breaths.

The tremors lingering in her body were dizzying.

Her heart pounded wildly.

Ever since becoming a Master, her heart had never beaten this fiercely.

Was this how a certain ancient soldier felt, who, after sprinting with all his might to deliver news of victory, finally met his end with a smile at the limit of his endurance?\footnote{the marathon}

Her heart was beating so hard that it almost seemed ready to burst her body apart.

Yet the immense sense of accomplishment made her mind clear and pristine.

\textit{Something about it... was incredible.}

\textit{And it also felt so… How do I put it? Refreshing?}

Qing's eyes became serene and gentle.

She almost looked like a monk who had attained enlightenment.

\textit{Now then. I have to wrap it up, but…}

\textit{Something about it feels so trivial…}

Qing's body and mental state were no different from someone collapsing after sprinting to victory.

At that moment.

"Uh, hey, um… You know…"

"Hm? What?"

"About the finishing touch… Since Junior Sister is strong enough, if it's alright with you, could I, uh... do it instead?"

Qing looked up at Jian Buxi.

She kept glancing at the servant lying on the floor, who had over two hundred points of Evil Karma.

Qing quickly understood her intention.

\textit{Ah. You enjoy killing too, huh?}

"So you want to have some fun too, is it?"

"Only if it's okay with you, Junior Sister…"

"Well, go ahead."

Because she was so immensely satisfied, Qing didn't feel like spilling more blood.

"Huh? Really!? Then, how much should I leave behind?"

\textit{What? Leave behind? Leave behind what?}

\textit{What kind of creative and systematic slaughter process are you planning?}

\textit{Are you saying you'll leave the last hit for me or something?}

In curiosity, Qing responded.

"Just finish it all. But can I watch?"

"Huh? Ah! That's a bit embarrassing, but... I guess it can't be helped."

Jian Buxi tore off a piece of her skirt and tightly wrapped the crushed wound.

\textit{Oho. She's going to start it off by stopping the bleeding?}

\textit{Is she a torture expert or something?}

\textit{It's like she's in a whole different realm compared to me.}

\textit{Maybe I can actually learn something today.}

And then, Jian Buxi opened the door where her Senior Sister was previously standing, pushed her inside, picked up Qing, and went in, locking the door behind them.

Qing's eyes sparkled.

\textit{Oho, she's even getting a whole room for herself?}

\textit{Dismemberment? Is it dismemberment? Can this possibly be some anatomy demonstration?}

Qing had huge expectations, full of anticipation for what she could be shown.

And then-

\textit{Ah. It isn't a slaughter.}

Qing realized she had harbored a ridiculous misunderstanding.

Why? Well, because what was unfolding before her was a vivid scene of Collect Yin Supplement Yin.

However, Qing also felt rather chagrined. Or rather, wronged.

\textit{No, like… How was I supposed to kn- Oh? Oooooh, oh wow...}

\textit{Wait, rubbing that there like that is a bit…}

\textit{Oh my goodness. How shameless. It's making me all shy.}

\textit{Woah, wait, this is so much more intense than the videos!}

Though Qing pretended not to watch Jian Buxi's ‘finishing touches', she actually observed quite closely with side-eyed glances.

All in all, it was a rather… fierce and intense.