\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (7)}

They set out dog food and labeled it as fried rice.

According to Qing's common sense, fried rice was stir-fried rice.

So, there should be no broth in fried rice!

However, the cook of the Bliss Palace did not seem to agree.

Qing, who always took food seriously, got angry.

\textit{No, how could they...?}

\textit{This fucking dog food is called fried rice?}

\textit{This is a dish that shouldn't exist in the world!}

\textit{Something as terrible as this should be rid of immediately.}

So Qing did just that.

She tried her best to get rid of it.

"Junior Sister Xi!? How, how can you eat five bowls of this? Are your legs perhaps not the only thing that's uncomfortable? Is there something wrong with your tongue as well?"

Upon witnessing this, Jian Buxi looked at Qing with startled eyes.

Qing had a resentful expression.

"It's because you grew up without any hardships, Senior Sister. Even though I have gone through a lot of hard times, calling this savory is fucking bullshit. It's disgustingly tasteless and…"

Qing ate five bowls.

"How could they do this… How could they make people feel so miserable while eating…"

Qing made a tearful face.

It was because she had a lot of grudges about food.

Seeing that expression, Jian Buxi spoke.

"Cheer up! Ah! Junior Sister, shall we go out for dinner tonight!?"

\textit{What's this? Why is there suddenly a halo shining around her?}

Qing brightened up.

"Really? Is that okay?"

"Starting from the Fifth Disciple of the Second-Grade, we can eat out."

Jian Buxi became the Fifth Disciple of the Second-Grade after devouring the boob pincher.

"But… Senior Sister, you don't have money."

Yesterday, she tried to buy some snacks while on reconnaissance.

However, Qing had lost both the Moonlight Sword (No. 8) and her Fushen-di, so she was completely broke.

To make things worse, Jian Buxi was also broke.

As such, they couldn't do anything besides suck their fingers sadly.

But suddenly, she had money today?

Jian Buxi answered.

"We can just earn it during the afternoon training, right?"

Qing tilted her head.

"Is money given while training? What in the world? Why didn't I receive it?"

"Ah. You don't know because you're from Zhongyuan, do you? In our Bliss Palace, you can earn pocket money while training! That's why I joined here!"

"What! Such an advanced system exists in the Bliss Palace?"

The situation in the Bliss Palace was a complete shitfest.

So was this the reason why the disciples endured despite that?

Qing recalled the terrible winter she had.

If she could earn money through training, Qing should have already become rich.

"Junior Sister, with your king-sized chest and pretty face, if you hang a red lantern, the customers will swarm in! Don't men secretly like big ones, after all?"

Qing blinked.

She thought she heard something strange. Very, very strange.

King-sized chest, beauty, red lantern, customer, popularity, men.

Combining each word, it seemed almost like...

"Wait. Can you just stop right there? I kinda feel something ominous. I don't think I should hear more."

"Well, Junior Sister is a Master, after all! Siphoning off a bit of True Qi doesn't satisfy you, right? If you wish, you can suck it out of men to your heart's content. I'm jealous..."

She asked to stop, but she ended up spilling everything.

Thinking back, she did say something like that, didn't she?

About how every time she managed to lure men with difficulty, the Senior Sisters took them all.

\textit{So that's what it meant.}

\textit{Well, I already saw her devour a woman.}

It was a very… intense sight since it was so direct.

If they can devour women, who says they can't devour men?

Qing swallowed hard and asked.

"Can I watch the training from the side?"

"No. Unexpectedly, It's full of pretty shy guys, you know? If they know someone is watching, they won't come."

\textit{Ah. This doesn't work, huh…}

Qing decided to change strategies.

"Then, if I catch a man and bring him to you, can I watch from the side while you do the finishing touches?"

"Eh!? Really!? I would love that, of course! Hehe..."

\textit{Ooooh, a reservation for a direct view!}

\textit{An exclusive performance in a VIP seat!}

With great anticipation, Qing thought.

\textit{Should I pop some corn in advance?}

\textit{If I watch while drinking cool Longjing tea, sheeeeesh!}

She should ask Xue Ganom tonight.

To recommend a bad guy with some very good stamina.

At first, Xue Ganom seemed like a weird name, but wasn't it kinda nice to say? It rolls right off the tongue.

It somehow evoked a sense of familiarity.\footnote{Ganom is a Korean word}

Perhaps it was actually a wonderful name?

His cold reasoning and insight could be said to be someone who wanted to dip from the Demonic Cult.

To be fair, he was actually a part of the Demonic Cult, but he wasn't a Demonic Cult disciple, so it did make sense.

\textit{Yeah, I should ask him what martial art I should learn if he had to choose just one.}

\textit{In order to prepare for the next 2000 Point exchange.}

\textit{It's best to listen to various opinions and decide, after all.}

Qing looked up at the face of Crutch No. 2, who was carrying her to her room.

\textit{Mmm. No need to ask this one, though.}

"Junior Sister! Then take some rest!"

Crutch No. 2, who put Qing on the bed, waved brightly and left for training.

Qing, lying on the bed, thought.

\textit{What to do now? Should I train?}

\textit{But, I'm so full...}

Qing gently rubbed her bloated belly, feeling the fullness.

Come to think of it, she should sleep a little if she's going out at night.

What if she makes a mistake because she's tired and sleepy at night?

So, she must sleep now, even if she has to force herself to.

"Heuaaah..."

Qing yawned and closed her eyes.

There is a certain happiness in lying down with a full stomach.

And to achieve it, she must lie on her left side.

Lying on the right side makes her stomach uncomfortable, after all.

With that, she laid down comfortably. And as her whole body relaxed and her mind felt drowsy...

-Thud, thud, thud!

\textit{Ah shit, who's knocking on the door at this ungodly(not really) hour.}

-Thud, thud, thud, thud. Ximen Qing!

\textit{Forget it. Ximen Qing is sleeping. Come back next time.}

-Thud, thud, thud, thud, thud, thud! Ximen Qing! I know you're inside!

"Fucking he- ssseup."

Qing abruptly got up.

"It's not locked, so come in!"

At that, the door opened, and a stranger stepped in.

She was a gaunt middle-aged woman, practically the very incarnation of a strict teacher from classical literature.

Even with that thin face, her spite was ever so apparent.

She seemed to be accompanied by a maid as well.

The woman clicked her tongue as she looked at Qing.

"Tsk, tsk. This wench is lying down after lunch. Did your parents not tell you that you will become a cow if you act in such a way?"

"Are you disrespecting cows right now? Cows are our friends, though."

"Well, no wonder you make such actions. Seeing from those vulgar udders, you have already become a milk cow. How could the Supreme choose this kind of a wench..."

Qing frowned.

\textit{The fuck? Why do they keep yapping about my breasts? It's not like they're fucking theirs.}

\textit{Do they think I like them or something?}

\textit{They're heavy, sweaty, obstruct my view, get in the way while swinging a sword, hurt no matter which side I lie on, and stain the front of my clothes if I spill food while eating…}

\textit{There's not a single fucking advantage.}

"What's this? Did you come to pick a fight? Wanna go?"

Qing raised her fist.

The woman shook her head.

"I am the teacher who will teach you etiquette from now on. You will call this lady, Madam Kang. People in Zhongyuan used to call me the Peerless Beauty, the natural enemy to all who hold allure."

"...? Beauty? Not a witch?"

Madam Kang's face twisted.

But Qing stood her ground.

If you didn't want to be shat on, you shouldn't have accumulated Evil Karma.

"How dare you! Will you not show respect to your teacher?"

"Teacher? I didn't even sign up for this class, though? Why are you suddenly my teacher?"

"Here. Take this for now."

At Madam Kang's signal, the maid brought a large bundle and placed it on the bed.

When Qing unwrapped it, booklets neatly piled up revealed themselves.

"What is this? A book delivery?"

"There are nine martial arts you need to learn, and one is a music score. Learn the martial arts by yourself, and I shall teach you etiquette."

It was a bunch of Fairy Arts bestowed by the Alleged Supreme.

Of course, one can do no wrong when bringing martial arts.

Qing immediately brightened up.

"Martial arts? Aw, you didn't have to."

Qing quickly glanced through the martial arts books.

Upon checking them, eight martial arts were registered.

\textit{One book seemed to be a trap, huh.}

\textit{Well, it's a freebie anyway.}

But the quality is fucking trash.

Five White Borders, two Blue Borders.

And one Red Border.

White, Blue, Red, Gold, and Purple.

By the modern-day standards of unscrupulous game developers who have a hard-on for shitty gambling, they could essentially be translated to N, R, SR, SSR, and UR.

The first two grades were held in contempt.

After all, the White and Blue ones ended at 10-Stars in order to reach the Grand Star with little to no Ability Points.

Compared to martial arts Red or higher, which granted enormous stats at the Grand Star when reaching 12-Stars, they were nothing more than all show and no substance.

Instead, they required a very low amount of Practice Points.

Especially the White Borders, which could be maxed out to 10-Stars as soon as they were obtained.

As Qing had always done whenever she got a White Border.

Well, at least there was one Red martial art.

Lustful Immortal Disrobing Dance.

Qing's face crumpled.

\textit{What the fuck? Disrobing? Is this a martial art for stripping? No fucking shot.}

Surprisingly, Qing's guess was mostly correct.

If one were to score how accurate she was, it would be about eighty points.

Disrobing was indeed that kind of disrobing, but the last character was the character for dance, hence why she was deducted twenty points.

Lustful Immortal meant a lecherous immortal.

It was also the nickname of Daji, who was dubbed the Most Evil Woman Under Heaven among the Three Beauties of Ancient and Modern Times.

Daji was an exceedingly beautiful girl who spent her days looking at the sky with a sad expression.

Originally, Daji was a Fairy living in the heavens, but she was punished and cast down to earth due to her wicked nature, thus longing for the home she could never return to.

And King Zhou spared no effort to console Daji's heart.

One day, Daji saw a person dying.

Upon seeing this, Daji smiled.

Upon seeing this, King Zhou had an unbelievable theory. As such, he observed a bit more and found that the more cruel and painful the person's death was, the brighter Daji's smile became!

So, to keep Daji's smile, King Zhou used all kinds of creative methods to torture and kill people.

It was such a beautiful story of pure love that it remained in history.

Eventually, Daji was moved by these efforts, and when enough blood had flowed to fill a lake, she began to strip off her clothes, seducing King Zhou and offering him a passionate night.

That was when a special performance of Daji's disrobing dance unfolded.

And the Lustful Immortal Disrobing Dance was created by modeling that sentiment.

Qing wondered if the disrobing mentioned was indeed that kind of disrobing.

\textit{If so, what's the use of learning this?}

\textit{Should I have Crutch No. 2 try it out before?}

Right as such thoughts were going through her mind...

"Focus! The teacher is not one with much spare time. We will start the lesson immediately. Take this."

Madam Kang threw a long object.

Qing reached out and caught it.

This cold and heavy sensation…

It was the unique chilly weight of the Ten Thousand Year Cold Iron.

Qing let out a burst of joy at this welcome sight.

"My Ten Thousand Gold! You've returned!"