\chapter{Heavenly Demon Divine Cult Serial Murder Case: The Night Of A Murder Without A Culprit (4)}

Tian Shan Divine City.

It was the main base of the Heavenly Demon Divine Cult, as well as a city built by the survivors of the Fire Worship Cult.

Tian Shan Divine City was larger than most medium-sized cities.

The city's population was diverse.

Descendants of the Fire Worship Cult, nearby barbarians, refugees from Zhongyuan who had converted to the Divine Cult, and disciples of the Unorthodox Faction and Demonic Path who had moved due to persecution.

Additionally, there were also technicians and their families who had been kidnapped and unwillingly settled there.

Thus, with its population, territory, and numerous armed groups, the Heavenly Demon Divine Cult was like a small nation of itself.

However, the Heavenly Demon Divine Cult had a significant problem.

Ever since the Celestial Martial Emperor stole their Divine Arts and hid them somewhere, there was a Supreme, but no Heavenly Demon.

A Heavenly Demon Divine Cult without a Heavenly Demon!

It was like a meat bun without meat.

Yet, even without meat, it still looked good on the outside.

They had placed a legitimate heir on the throne as the Supreme.

Nevertheless, it was still just a ruler without Divine Arts.

Listening to Jian Buxi's explanation, Qing nodded in agreement.

"You're talking about the Alleged Supreme, right, Senior Sister?"

"Yeah! Huh!? No?! You can't use such bad words!"

Surprised, Jian Buxi covered Qing's mouth.

The Alleged Supre... No, it was blasphemous to even say it.

​​If the enforcers of the Discipline Hall, or even other Senior Sisters, heard it, they could be beheaded for such remarks.

Qing emphasized through her blocked mouth.

"Aweged Supweme."

"Ssseup. No. Don't. You shouldn't say such bad words. Bad girl."

\textit{Exactly who was calling whom a bad girl?}

Qing was so dumbfounded that she kept silent.

"The Supreme is currently in an incomplete state. However, once we retrieve the Divine Arts!"

"Then?"

"The Supreme has blocked his meridians and sealed his dantian himself. Once he recovers the Divine Arts, he will overcome Qi Deviation and soar beyond the Demonic Descent Realm to become the future Heavenly Demon."

It seemed like the Natural Realm Wannabe had that type of setting.

However, to Qing, it sounded no different from a gambler boasting they would repay their debt.

By the way.

"Soar? You know about such an advanced word? Do you even know what it means, Senior Sister?"

"I don't! I heard it during our lessons!"

And this was the downside of rote education.

"When that day comes, the 100,000 Divine Cult disciples led by the strongest Heavenly Demon in history will sweep across Zhongyuan, defeating the oppressors and fanning the holy flames of the Divine Cult!"

\textit{What? Their mindset was more akin to the Qianlima than the Heavenly Demon.}

Qing asked again, dumbfounded.

"What will you do after fanning the Divine Cult's holy flames?"

"Well, obviously, I don't know anything! I'm sure the higher-ups would know!"

\textit{Well, I guess, it was good if she was all sunshines and rainbows about it?}

\textit{Anyway, the Heavenly Demon Divine Arts, was it...}

Qing summoned the Martial Arts Window.

Search for Heavenly Demon Divine Arts.

Then the Martial Arts Window complied.

\begin{quote}
\underline{Martial Arts}
\medskip

Heavenly Demon Cultivation Technique

Heavenly Demon Qi Circulation Technique

Heavenly Demon Sutra

Heavenly Demon Hell-Slaying Technique

Heavenly Demon Celestial Qi

Heavenly Demon Thirteen Swords

Heavenly Demon Serene Divine Sword

Heavenly Demon Asura Divine Sword

Heavenly Demon Iron Demonic Path

Heavenly Demon Absolute Rhythmic Path
\end{quote}

There were ten entries on one page.

Qing turned to the next page of the Martial Arts Window.

\begin{quote}
\underline{Martial Arts}
\medskip

Heavenly Demon Asura Demonic Path

Heavenly Demon Death Piercing Spear

Heavenly Demon Six Fists

Heavenly Demon Divine Fist

Heavenly Demon Heaven-Sealing Palm

Heavenly Demon Hand

Heavenly Demon Destructive Hand

Heavenly Demonic Earth

Heavenly Demon Eternally Prosperous and Radiant Nails

Heavenly Demon Dominion Steps
\end{quote}

And then another page.

\begin{quote}
\underline{Martial Arts}
\medskip

Heavenly Demon Phantom Steps

Heavenly Demon Submerging Technique

Heavenly Demon Flying Technique

Heavenly Demon Palm

Heavenly Demon Forbidden Technique

Heavenly Demon Royal Coiling Power

Heavenly Demon Starry Thunder of Yin and Yang

………

……

…
\end{quote}

There were thirty-seven martial arts across four pages.

And they were all in Purple, to boot.

\textit{Wait, what the, what the fu- what is this?}

\textit{Why are there so many Purple Martial Arts? What worth do the other Purple Martial Arts if there are so fucking many?}

\textit{And why are there so many Sword Techniques and even more Half-Sword Techniques?}

\textit{Is it a requirement to have a servant carry your weapons around or some shit?}

\textit{What? You want to use them alternately or something?}

Annoyed, Qing closed the Martial Arts Window.

Ximen Surin said that the Absolute Studies of Divine Arts were something that people couldn't master even if they trained their whole lives.

She had previously guessed that the standard for those Absolute Studies was probably around Purple. Yes, she did. But…

Even with Qing's cheat-like martial arts, the training speed for martial arts with a Purple Border was completely different from those below.

They consumed two and a half times more Practice Points than the next lower tier, the Gold Border.

\textit{How the fuck am I supposed to master those thirty-seven purple martial arts? When will I have the time to?}

\textit{Am I supposed to pick and choose only what I want?}

Qing asked Jian Buxi.

"Senior Sister, what's the most famous of the Divine Arts?"

"Of the? Most? Junior Sister. There's only one Divine Art. Heavenly Demon Divine Arts! The one and only whether above or below the heavens! Gongjeonjeolhu! Bukdudaesung! Gogeumbujae!"\todo{translation}

"Do you perhaps… know what all that means?"

"Of course! It means that it's extremely great!"

\textit{Nah, she's a lost cause.}

\textit{She doesn't know shit.}

\textit{I'll ask Gramps later, I guess.}

"Forget it. Anyway, I want to look around the city, you see."

"Sure! Have a good time!"

Qing's eyes narrowed.

\textit{What? Is she refusing to be a Crutch?}

\textit{What value does a Crutch have if it's not held by someone evil?}

Qing delivered an ultimatum.

"Senior Sister should carry me, yes?"

"Ehhhh!? Me!? Why!?"

Jian Buxi asked back vehemently.

\textit{By the way, why is she always so noisy...?}

"Isn't it natural for Senior Sister to take care of a Junior Sister with a bad leg?"

"What!? Nonsense! Why should a Senior Sister take care of a Junior Sister?"

"Then what do Senior Sisters do?"

"Uh, they gather Junior Sisters when they're bored and scold them, press their solar plexus, or kick their shins? Or they use them as chairs or tables, make them clean, do laundry, bathe them, and take away any men they catch."

"……?"

"Oh, right. Since Junior Sister needs to be careful from now on, I'll let you know this, just for you. You need to be cautious when Seniors that are Second-Grade disciples call for you."

"When they call for me?"

"Senior Sister Ok always pinches my chest, but then says I'm pretending to be hurt and whips me. But you shouldn't endure it either; last time Senior Sister Ham held out, and it got torn off completely, you see. So when Senior Sister Ok calls you, you should pretend it hurts right off the bat. And Senior Sister Dab makes you eat raw meat, and if you vomit, she makes you swallow it back, so..."

Jian Buxi explained about the Second-Grade disciples to be wary of.

While occasionally showing countless scars on her arms and shoulders as she did.

It was the ultimate evolution of hazing.

Of course, the Bliss Palace disciples had their own reasons.

They also suffered from their Seniors, so they wouldn't understand why they were being singled out for doing it as well.

Then, when they joined factions, they were advised to instill fear by tormenting the kids, saying that otherwise they might not know when they will try to stab you in the back. This was the reality of the law of the strong.

Originally, hazing was passed down as a form of tough love.

And even among them, the weakest and most docile Jian Buxi was everyone's target for venting their frustrations.

She did not have a single intact place on her body except for her face, neck, hands, and feet.

Qing was disgusted.

\textit{Is that seriously what Senior Sisters are supposed to do? Then?}

"So, you're saying you're going to do that to me now?"

Qing quietly drew up her True Qi.

The ever-aggressive Purple Lightning Qi burst out from her dantian as soon as she willed it.

"I was going to, but you're already cripp, I mean, ah. Sorry. Your leg is injured, so I feel sorry for you."

Qing withdrew her True Qi.

Her Purple Lightning Qi seemed to hesitate before returning.

\textit{What the hell?}

\textit{What kind of life had she lived so far?}

"Then it seems you'll just get beaten if you stay here anyway. Wouldn't it be better to come with me?"

"But if I get caught leaving my post, then tomorrow..."

No wonder she disappeared after breakfast.

She must have been dragged around all day.

\textit{Eh? Wait. Then what about me?}

\textit{Aren't I the youngest now? They didn't call for me, though?}

When Qing asked about it, Jian Buxi laughed sillily.

"Hehe, actually, they told me to bring Junior Sister, but you just got here and haven't adjusted yet, so... And your leg is injured..."

Qing was flabbergasted.

\textit{So this retarded bitch ruined all my fun time. That's what that means, doesn't it?}

"Ha. What a complete retard."

"Huh!? Huh? What? Me...?"

"You're going to drive me crazy. Crazy, I tell you. Why are you living like that?"

"Huh. what, w-what did I even do..."

Jian Buxi made a tearful face.

Qing sighed deeply.

"That, who was she again? Senior Sister Ok? Did she call for me too?"

"Huh? Yeah..."

Jian Buxi answered hesitantly.

Qing spoke with an unyielding firmness.

"Enough. Carry me to her."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ok Hwahwa was the Fifth Disciple of the Second-Grade.

She was favored by the Fourth Disciple of the FIrst Grade, Yeom Heeji. and was part of that faction, acting as the faction's disciplinarian.

After having dinner, she was bored and thought about calling someone to discipline.

Just then, someone knocked on her door and shouted loudly.

-Senior Sister Ok! This is Junior Sister! From the Third-Grade! Jian Buxi!

Ok Hwahwa contemplated for a moment.

Jian Buxi wasn't all that fun to bully.

She was a simpleton without any malice or guts, just crying silently like an idiot.

Even just this morning, hadn't she disciplined her because she talked back and refused to bring the new youngest?

Yes, she wasn't any fun at all.

\textit{No skills, No fun facto... Hm? Wait. Or maybe not?}

\textit{Hadn't she been promoted to the Seventh Disciple of the Third-Grade just this morning?}

Ok Hwahwa considered for a moment.

\textit{Maybe I can talk to Unni about bringing her over to our side?}

Jian Buxi's voice called out again.

-As instructed! I have brought Junior Sister Xi!

Ok Hwahwa tilted her head.

\textit{Junior Sister Xi? Her name was definitely Ximen Qing. Then wouldn't it be Junior Sister Ximen?}

Menqing wasn't an uncommon name.

But it wasn't a name that a Xi family would give to a daughter.

It would be confusing since it sounded similar to the Ximen family's name.

Still, well, it wasn't like it was impossible.

"Come in."

-Yes! Jian Buxi! Of the Third-Grade! Coming in!

\textit{Very well then. Let's see what the newest recruit looks like, shall we?}

Ok Hwahwa smiled wickedly.

But unfortunately, it would take some time to confirm the new recruit's face.

Because just as the door opened and she tried to see how she looked…

Suddenly, her shin went Prick.

The other shin went Prick as well.

"Ouch."

Ok Hwahwa let out a rather cute sound and bent over.

She saw binyeos, used as hair ornaments, sticking out of both her shins.

\textit{Huh? Wait. Why are these stuck there?}

Only after seeing the wounds did the excruciating pain hit her.

Ok Hwahwa took a deep breath to scream.

"Keuk. Heuk."

Then, it almost seemed as if she heard a bell, as a blow struck her upper abdomen, making her exhale sharply and roll off the bed.

The dinner she had just eaten came rushing up.

"Senior Sister. Close the door."

"Okie! Got it!"

Click. The door locked.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was pleasantly cool from the early evening of the summer, probably because of Tian Shan Divine City's high altitude.

Qing, nestled in Crutch No. 2, had an infinitely clear gaze.

"Hmmhm..."

Crutch No. 2 also seemed to be in a good mood.

Along with unusually glossy skin, she hummed a tune with a bright expression akin to the sun.

The younge- No, the Seventh Disciple of the Bliss Palace Third-Grade disciples, Second-Rate martial artist Jian Buxi no longer existed.

Instead, there was only Jian Buxi, the Fifth Disciple of the Second-Grade and a martial artist who had just stepped foot into the First-Rate Realm.