\chapter{On the Way Home (7)}

After finishing the New Year's greetings and returning to the Sichuan Tang Clan manor, as soon as she passed through the round main gate of the guest hall, the pitter-patter of short-legged footsteps grew closer from somewhere.

There was only one little kid staying in the guest hall.

Qing opened her arms wide towards the approaching Ciyu.

But Ciyu, who had been running, screeched to a halt in front of Qing.

And then, she widened her round eyes, already tinged with dark circles, even further.

"Oh, ooh, ooh."

"Huh. Why?"

"Pretty. You're so pretty."

\textit{Come to think of it, I supposed I had never really worn makeup in front of Ciyuo.}

\textit{But, pretty?}

\textit{My dignity as a dad, is this okay?}

"Makeup, I want to do it too. Do it for me."

A sudden 'do it for me' declaration!

Ciyu's eyes, looking up at Qing, sparkled brightly for the first time in a long while.

Qing let out a small, breezy laugh.

She had been worried because the child was too gloomy, but it was just that her eyes were dead and her dark circles were deep,  for a normal kid of this age, this was a natural reaction.

"Does Ciyu want to wear makeup too?"

"Yes, yes."

"For that, you have to go to an expert. Come on, let's go to Yi-mei."

"Why? You won't do it? Yi-mei will do it?"

"Yi-mei\footnote{Older sister}? Isn't she your aunt? Hmm, I don't know. Anyway, Yi-mei is the expert at makeup, you know? I didn't do this either. By the way, what was Ciyuo doing? Were you playing hard and having a blast?"

At that, Ciyu placed her tiny fists on her waist and puffed out her chest, showing off.

"Me, me. I was studying."

"Gal!"

Startled, Qing let out the exclamation without thinking; now that she was about ten years into her murim life, her exclamations had also become those of a martial artist.

Of course, 'Gal' was the character for 'to scold', a rebuke closer to 'You scoundrel!'

"How can you be so praiseworthy! Ciyuo has finally become a person, huh? Was it San? It was San, right?"

"Yes. Handsome Mom."

"As expected, there's no one like San. Anyway, as for the other guys, I made them moms, but even though their daughter is illiterate, they just lazing around, stretching their legs and sleep soundly."

The other mothers might feel it's unfair.

For the one who was lazing around the most to be saying such things.

But it's the way of the world to even curse the king behind his back, and besides, Qing was a person with the character to say it to their faces.

Qing picked Ciyu up in her arms.

"Come on, let's go. We have to get you all pretty and show off to your handsome mom."

"Hehe, keukeukeuk……"

\textit{Though I wish she wouldn't laugh like that.}

As she crossed the yard, a door slid open right away.

Of course, it wasn't because an expensive primitive Zhongyuan-style mechanical automatic door was installed, but because a person opened it.

Somehow, a stern, solemn, and serious-faced Paeng Daesan revealed himself.

"You've rested? Then-"

"Hey, teacher. Our kid is much obliged to you. By the way, when do you think she'll be done with the Thousand Character Classic?"

"……"

Meanwhile, Paeng Daesan's mind went blank!

And for good reason.

The difference between a luxury item and something that merely looked like one lay in the very small details, the trivialities.

So, if you add even smaller details to an already existing luxury item, wouldn't it become a super-luxury item?

Qing's face was currently in a state that no man could tear his eyes away from!

Especially her lips, a lone profusion of red on a whitened face, a glistening sheen, as if only that bewitching lower face filled his entire vision.

"Hello? San? Friend?"

\textit{What's this? Is he broken? No response?}

Qing reached out and waved her hand back and forth in front of Paeng Daesan.

Then, Paeng Daesan's voice somehow dropped to a low register.

"……Going to the King's Manor with powder on your face. Was there someone you wanted to show it to?"

"No, they did it for me there. What's there to show? What good would it do me to show off a powdered face?"

"Then you can just wash it off."

"But the maids at the manor put so much effort into it, I feel like it's a bit much to just wash it all off?"

"Those people were just welcoming a guest who was paying respects to the prince, to His Highness. Isn't that just what they do as part of their job?"

"Well, I suppose so?"

"Isn't it uncomfortable? My sister absolutely loathes wearing face powder."

"Hmm, it is uncomfortable. It's annoying too, and it feels weird to have something's on my face, and I can't even touch it, you know? It also rubs off if I wear a face veil."

This was the reason Qing went around bare-faced despite receiving countless super-painful noggin-smacks from Ximen Surin (she did it after being hit).

Qing was the type to touch her head often.

Scratching the back and sides of her head was basic, she also scratched her cheeks, her chin, and the ends of her eyebrows—a very bad habit for skin health.

If the colors smudged or came off, she would have to fix her makeup.

And when she wore a face veil, it inevitably brushed against her face, and those areas with smudged powder made her vision messy.

If you think of the face veil as the glass of a pair of spectacles, you would know how it feels.

"Hmm, well, it's not like it's anything worth showing off. Oh, I'm taking Ciyu for a bit, okay? She seems to want to try makeup. Hmm, I wonder if putting powder under her eyes will cover up the dark circles a bit."

And so, Ciyu's first makeup experience in her life!

For reference, Ciyu, with the dark shadows under her eyes covered with white powder, didn't quite look like Ciyuo.

The dark circles under her eyes had been packaging her dead gaze as tiredness!

It truly held the subtle principle of fighting poison with poison and using barbarians to fight barbarians.

But after brightening the area under her eyes, hmm, she just looked like a little kid with dead eyes.

Of course, it's hard for a kid of this age not to be cute in any state.

"Oh my, our Ciyu, who do you take after to be so pretty?"

"Kihihi, I want to go to my moms."

"Why, to show off your makeup?"

"Yes, yes."

"Hmm, your moms are training, so shall we show them at lunchtime later?"

\textit{Gunyeong is always diligent in building up her pathetically meager Inner Qi whenever she had time.}

\textit{Well, it's true that Gunyeong is in a position where she had to put in some effort.}

\textit{What could she do with that millet-sized Inner Qi.}

\textit{But Lan-Ah's deep dive into training is a bit, no, very unfamiliar.}

\textit{She used to stick to my side all the time, making a fuss about going out to play, but now it's like she's suddenly matured. Hmm, it feels a bit empty.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Two days later.

Tang Lan-Ah, who had come to see her off at the canal, held onto Qing's hand.

"Qing'er, stay a little longer. Please?"

"Hey, Lan-Ah, you're busy with your training, what's the point of me just hanging around someone else's house? Still, you're making a lot of progress, right? You have to focus when you get that feeling."

"Then, see you at Divine Maiden Sect later."

Usually, Tang Lan-Ah would have been wailing and crying, not real tears, of course, but pretending to cry with fake tears, making a scene, saying 'just kill me, walk over my dead body.'

But she backed down obediently, as if she had just thrown it out there to see what would happen, thinking it would be nice if she stayed longer, but if not, no harm done.

Because Qing had claimed to be immune to all poisons.

\textit{Come to think of it, if poison doesn't work on Qing'er, what's the point of me accompanying her? Just look at this recent incident. If my Poison Arts were at a higher level, Qing'er wouldn't have had to go into enemy territory all by herself.}

And so, amidst the send-off from the Tang Family, the boat heading for the Yangtze River raised its anchor.

Riding the canal to the Upper Yangtze.

The Upper Yangtze merges with the Yangtze River downstream, and soon the Yangtze flows along its winding path.

A three-day boat ride from Sichuan brings one to the end of Sichuan land, the entrance of the great gorge of the Yangtze, Qutang Gorge, at the border of Hubei province.

If you wait for half a day while admiring the dizzyingly high cliffs on both sides, a peak resembling the elegant back of a woman suddenly reveals itself on top of one of the cliffs.

It was the famous Divine Maiden Peak of Qutang Gorge.

And what lies beneath Divine Maiden Peak?

Hmm, wasn't Qing's thatched cottage, though small, her own home, her sweet home, located right behind Goddess Peak?

So Qing's heart also felt somehow relieved.

Ah, home, she thought.

\textit{But my home is right there, yet I have to take a detour, isn't that a bit of a pain?}

\textit{Maybe I could lower a ladder down the cliff, but then it would be a problem if random riff-raff climbed up, so of course, that is out of the question.}

And when the cliffs stretching on both sides of Qutang Gorge end, a wide view of a pier unfolds on the riverbank beyond, the pier of Zigui County, which seems to get more prosperous every time she comes, comes into view.

And so, Zigui County!

On the way to the Xue Family Trading Company, its employees greeted her with very, very enthusiastic greetings of 'Welcome, Young Lady', and finally, she stood under the large signboard of the Xue Family Trading Company.

Someone among the staff must have quickly spread the news, as Cui Liwen, who came out to greet them, saw the group and said with a very bright smile.

"Oh, Ciyu'er, you've come? Come to grandpa. Aigoo, they say one improves day by day, and now I see you've become quite a lady."

"Hihi, kihihi."

"Huh."

"What are you doing? Not coming in? Tsk, I thought you'd at least be back for the Spring Festival, but you left last year and came back this year? You heartless thing. There's a limit to being indifferent. Ciyu'er, you mustn't be like your father. Got it?"

"Yes, yes."

Cui Liwen clicked his tongue loudly with a tsk and entered the trading company, holding Ciyu.

Qing could only stare blankly at Cui Liwen's back.

"Ugh."

\textit{What on earth? What's with this cold shoulder treatment?}

In any case, like this, Ximen Qing, has returned!

As usual, she ate at the Seolga Trading Company.

She ate snacks and drank tea, and soaked her body in the newly built bathhouse. 

\textit{Hmm, the hot bath made of marble somehow reminded me of my hometown.}

The refreshed Qing entered a building of the trading company.

"You're here? You look well."

"Hey, where are you looking while greeting me?"

"Ah, so that wasn't your head. I thought it was strange that it was attached to both sides."

It was that Xue bastard, throwing out a tease the moment they met.

This was why getting used to things was so scary; since he was that Xue bastard who made a habit of teasing, she now just thought, 'I guess that's just how he is,' and felt no emotion at all.

Of course, she wasn't particulary impressed before either.

No, perhaps she was rather intrigued.

"Xue gets prettier every time I see him. I'm going to fall for you at this rate, for real. Have you been well?"

"What's the big deal about being well? Isn't living well just eating well, sleeping well, fucking well, and shitting well?"

That Xue bastard's expression was triumphant.

At that, Qing gave a thumbs-up.

"Ooh, you got me there. So, you must have been shitting a lot?"

"Hey, can't you at least pretend to be embarrassed? You're not some mischievous neighborhood auntie who's gotten old."

"I'd be glad if it were just a joke, you know? I've heard all sorts of things. Things you should hear, things you shouldn't hear, you haven't heard what those Unorthodox sect bastards say, have you? Someone like that Xue is being polite, I tell you."

"Hmm, my apologies. I have heard them too."

At that, Qing nodded.

Since he was a guy whose beauty bloomed more every time she saw him, he must have experienced plenty of the high-level insults thrown by those unorthodox ruffians and bandits.

"So, is it true? The mysterious man of Changbai Mountain?"

"It's not certain. However, there have been testimonies from Jurchen and Dongyi merchants. They say a monster lives at the foot of Changbai, its eyes are blood-red, and black veins bulge grotesquely, making it indescribably strange. It's as ferocious as a tiger, and if you give it a large beast, it tears it apart and eats it on the spot."

The bulging of black veins on the skin was a characteristic of the Reverse-Blood Demon, a representative side effect of the Pacheon-yeokhyeol-susim-jacheom-gyeol.

"All Demonic Arts are like that, but in the case of Pacheon-yeokhyeol-susim-jacheom-gyeol, it's even more severe. Reversing the Qi flow means, in other words, the principle of reversing the heavens, doesn't it? The natural order is for a lowly creature to accumulate virtue and be reincarnated as a human, but to do the opposite, a human must return to being a lowly creature like a beast. So I believe it must be a Reverse-Blood Demon."

"Umm."

A frown creased Qing's brow.

\textit{So the Reverse-Blood Demon is not in its right mind.}

\textit{It's good news that they found the master of Pacheon-yeokhyeol-susim-jacheom-gyeol. But if he's not in his right mind, is he in a state to be able to give up his martial arts?}

"Still, it's a wonder the rumor didn't spread, right? Even if it's a Demonic Art, if it's one of the ten great demonic arts of the world, wouldn't martial artists from all over the world have flocked to it?"

"Well, we are lucky because we intentionally investigated it, but a proper martial artist wouldn't have any reason to associate with barbarians, would they? Some may have overheard and caught on, but what loyalty do those who covet Demonic Arts have to spread rumors here and there? They probably went there and died."

Still, a sect that has made a name for itself in a region has no reason to bother associating with barbarians.

And, those who have perfectly good martial arts do not covet Demonic Arts, though it might be a different story if it were a top-tier Demonic Art, like the Essence Absorbption Demonic Art.

So, those who heard the rumors from the barbarians were likely low-level martial artists, and also desperate people who would even resort to Demonic Arts.

If such a low-level martial artist went all the way to Changbai Mountain to catch a Reverse-Blood Demon, well, what else could they do but die?

"Hmm. Well, what can you do? A thirsty person looks for a well, and if there isn't one, they have no choice but to go to the river or dig a new one. Anyway, thanks for looking into it. As expected, Xue Ga-nom. I might have to raise your intelligence rating. At this rate, you're the best intellect in the North?"

"It was nothing. I'm not someone who uses their head in the first place, what's with all this talk about intellect."

At that, Qing nodded her head.

\textit{This very humility is what makes Xue Ga-nom worthy being called the greatest intellect.}

\textit{Both Zhuge and Chunfeng were merely dying to show off that they've read a few books.}

\textit{Indeed, Xue Ga-nom, this is the mental discipline of a true intellect of this era.}

Then, that true intellect of this era uttered a joke full of harassment.

"Unless maybe you mean the biggest prick in the north."

"Oh, you're confident?"

"Why, want to take a look?"

"Ugh. No thanks. What's so great about it, you look at it a lot."

Anyway, since that's what he said.

It was the moment the first destination of her seventh year in Wulin was decided to be that end of the world, Changbai Mountain.