\chapter{On the Way Home (2)}

The road from Yunnan to Sichuan was surprisingly well-paved and quite comfortable.

Sichuan was a low basin surrounded by high mountain ranges, while Yunnan sat atop those high mountain ranges.

The elevation difference between the two regions was about six hundred and fifty zhang, and this tremendous drop did not decrease gradually but suddenly presented itself.

Despite the monumental sight, it was truly spectacular.

The winding mountain path stretches endlessly downwards, like the infinite writhing of a giant snake.

And the vast Sichuan basin can be seen entirely at a glance; one feels as if standing at the end of the world looking down.

Qing could not take her eyes off the breathtaking view.

\textit{The dark spots in the distance must be the city of Chengdu in Sichuan.}

\textit{The actual buildings appear as tiny as grains of rice, and no people can be seen. Indeed, from such a height, this view is a splendid performance. Like trash—}

"Can you come down a bit?"

A heavy bass interrupts Qing's grand monologue.

\textit{Hmm, it's a rare reminiscence of my hometown, yet I'm not particularly nostalgic or regretful about it.}

\textit{Still, isn't it fascinating that memories flash back like this occasionally?}

\textit{Like suddenly recalling childhood friends I had completely forgotten about or old schoolmates I hadn't cared about at all suddenly popping into my dreams.}

\textit{In fact, I might not be able to recall them, yet human memory is more sensitive than I thought, and perhaps if I meditate well enough, I could even contemplate the non-action of the martial artists I encountered during my time—}

"At least, answer me."

The tone has dropped lower than before, growling.

So Qing smacked her lips and opened her mouth.

"Uh, how about thinking of all this as training? Look at that Jeagal a bit. He seems quite excited."

"Hmm, this is a different form of stimulation. When I return to the sect, I will have to consider a mechanism for this."

Jeagal, leaning against the cart, trudging down the mountain path, puffed out hot breath in this chilly weather.

He was holding back his Inner Qi while supporting the cart to practice his physical cultivation.

Indeed, the hardships of the carriage journey from Yunnan to Sichuan began from this steep mountain slope descending infinitely.

This was because a carriage was far more dangerous on steep descents than on ascents.

Surprisingly, ancient carriages in the primordial Zhongyuan were equipped with braking mechanisms!

With a simple principle of wrapping the axle in leather and cloth to make it roll less easily, a carriage without such a braking device would face severe punishment according to strict national laws.

Zhongyuan were surprisingly demanding concerning safety standards for carriages.

In fact, even about two thousand years ago, during those very ancient dynasties, cart drivers had their driving skills assessed in both practical and written examinations, creating humanity's first driving license test.

If one failed this ancient driving license exam four times, they faced permanent disqualification and forced labor as a penalty, making the standards even stricter than those in Qing's hometown.

In any case, with just the installation of that primitive braking device, a road filled with stones could allow one to descend in a carriage without worry.

However, on mountain paths it became ambiguous: if the wheels slipped on the dirt path, a significant accident could occur.

So, people must dismount from the carriage.

They need to carefully check and take care of the horses.

If a cart was involved, it's better for someone to hold it while going down.

So, one must dismount to help.

This was not about viewing the scenery from the carriage.

In fact, Qing was quite diligent before others.

The moment one tried to be lazy and slack off, what's comfortable was but for a fleeting moment, and the lasting impressions were heated gazes and increasing whispers behind their back.

When alone, it's one thing, but it would be foolish to suffer damage to interpersonal relationships just for a moment's ease.

\textit{But, um, I think I now understand why everyone was so impatient because they couldn't get the hang of it…}

Following the advice of Ji Yun Zhenren, Qing worked hard, passionately, and did her best until they reached the entrance to the land of Sichuan.

Of course, Ji Yun Zhenren can be wronged.

'I just told you to do whatever you want, I didn't tell you to just spread out and become a worthless bastard who doesn't do anything.'

But Qing had her own reasons.

\textit{But since I don't do anything, how should I put it, I just end up doing nothing.}

\textit{Just like this, I feel comfortable spending time without meaning, and when I try to do something, I feel lazy and my mind doesn't move.}

\textit{And what if your heart doesn't move?}

\textit{Then you can't do it?}

Then suddenly.

"Wait. That's a little weird. Why is it only me? There's Lan-Ah too. She has never done anything anyway."

It felt just like the saying: the one who farts now is the one who gets angry.

It's quite childish indeed.

Why is only I am at fault when they're partying too!

In fact, when it came to moving cargo or overcoming the downhill paths with the cart, Tang Lan-Ah naturally exempted herself from such chores.

The unofficial princess of Sichuan, of course, never had to partake in such menial tasks nor had she ever thought that she should.

Xue I-ri also often excluded such duties, but in her case, it was closer to not being assigned because she was deemed unfit for the work.

Such was the sad nature of people.

Those who were diligent and help out were naturally labeled 'good people' in others' hearts.

So, they get tasked with work quite naturally.

people who always act like fools and do nothing with a straight face are just considered 'those who do nothing.'

So, they would probably just be met with disapproving glances and a tsk of the tongue before being ignored.

Conversely, those like Xue I-ri, who were not helpful, would receive a kind-hearted 'Oh well, at least they're breathing' and move past the situation comfortably.

Thus, the phrase 'working hard only leads to loss' emerged.

But was that truly the case?

Working during working hours doesn't equate to suffering a loss.

Just because one worked more than others at the same time doesn't lead to extreme exhaustion or a drastic shortening of lifespan, nor does any devastation of life occur.

Therefore, saying that working hard leads to a loss was merely a cowardly excuse for laziness.

Although.

There was one exception: overtime.

If as a result of hard work, tasks arose during non-working hours, it becomes significantly problematic.

Such transgressions were often common among many businesses in Qing's hometown.

For individuals working in such businesses?

It becomes essential to carry the mindset that working hard only leads to losses, following the principle that one must prioritize themselves before any company, focusing on personal health and development.

In any case, after hearing such childish remarks, Peng Daesan was momentarily left speechless.

Although it was childish in tone, it was also true.

However, admitting it with a resigned mood feels like an acknowledgment of defeat, so instead, he threw in a remark.

"Are you suggesting you're on those two's level?"

"…Ah."

Qing suddenly jolted awake!

\textit{Absolutely, that would not be acceptable.}

Qing leapt down from the roof.

Because the heart whispered to her.

No matter how much she decided to do nothing, there remained a minimum dignity, a minimal value that must be upheld as a person.

\textit{I shouldn't be on the same level as Guyeong and Lan-Ah.}

\textit{Normally, at this point, the little girl would start to grumble, asking what's wrong with her, and why is she being used like that, and would take out a bottle of poison from her sleeve.}

\textit{However, these days, Lan-Ah seems to have become deeply engrossed in the joys of reading.}

\textit{Who would have thought she possessed such a keen interest in study at such a young age, becoming a master in herbal medicine?}

\textit{Come to think of it, just lying around doing nothing isn't very comfortable.}

\textit{I don't even know what to do until I break through Harmony Realm, so I feel like I should just sit back and let my heart flutter.}

\textit{But, the annoyance just keeps increasing.}

\textit{My mind is getting anxious for no reason, and time is passing by without doing anything, but it feels like I'm getting more and more uncomfortable.}

\textit{First of all, I suppose I should put advice of Master Ji Yun aside for the time being.}

\textit{Letting go is good, but I should first clear the Status Window before deciding to fully let go…}

Had he knew about this, Ji Yun Zhenren would have surely become increasingly exasperated, feeling as if this wasn't the point.

Thus, the descent continues endlessly.

Down the winding path, there was even a camping site provisioned for rest, indicating that even martial artists could not speed through the experience of hauling a heavily laden cart down such steep hillsides.

After spending a day camping, they finally set foot in the Sichuan Basin.

Unlike the gentle lands of Yunnan, where double cropping or even triple cropping can be cultivated, Sichuan had a pretty chilly winter.

And thus, on the eve of the last day of the year, they arrived at the prestigious Tang Family of Chengdu!

Sichuan! Having previously visited, let's skip the explanation.

Chengdu of Sichuan! Again, let's skip this!

And thus, in Sichuan!

And thus, in Chengdu!

The Tang Family warmly welcomed their esteemed visitor, as the entire immediate family gathered.

Tang Lan-Ah was the most treasured child of the Tang Family.

As the saying goes, when you bite all ten fingers, there was no such thing as an unimportant finger—all children were treasured equally.

However, some children were more equal than others.\footnote{Reference to a line in George Orwell's 'Animal Farm'}

Particularly as every child born was another son, the rare appearance of a precious youngest daughter was even deemed more equal.

And Qing was the only friend of this precious daughter.

To the elders of the Tang Family, worried about their daughter's character, what level of reassurance comes from having at least one friend.

Of course, beyond that, Qing was a special guest of the Tang Family, a benefactor.

The family motto, stating that favors should be repaid double while grudges would exact revenge tenfold, was somewhat petty.

The somewhat petty nature lies in that this motto implies relative evaluation rather than absolute.

When repaying kindness, it was twice that of what another clan owes, but when repaying grudges, it was tenfold compared to another clan's revenge.

Thus, it provides at least a guarantee to treat one's benefactor at no less than twice as well…

However, the guest's treatment seems remarkably lackluster.

"Don't pass those pages yet; I haven't read them all."

"Really, uncle reads this slowly? I've read it three times already; is that enough?"

"You brat, wait until you grow older and see. Ah, I get your point. Next page."

"Wait. What on earth is that character? Is that 遺 (yu) for 'omit' or should it have been written as 遣(qian) for 'send'?"

"No, my brother. In context, it surely must be 'yu'. You have to leave the broken-down components in your body, right? Hmm? Or is it 'qian'?"

"I thought it is 'qian'."

"I saw it as 'qian' too."

"Isn't it 'yu'?"

It was a truly breathtaking sight of the head of the Tang Family and the immediate kins had gathered around, all peering at the text.

The catalyst for this was the cart of books brought by Heavenly Blossom Sword.

Among the many titles there, none dared pass by the main text, which was simply unmissable for any practitioner of poison…

The title was 'The Method of Overcoming the Limits of Poison Techniques'!

Even Tang Lan-Ah, who had been slacking, found herself engrossed, so it was quite impossible for the head of the Tang family to ignore the temptation.

And so, drawn in by the text, they unknowingly picked it up and opened it.

Although the family benefactor had arrived, why would the clan head be so captivated by a book?

Thus, the former and current clan leaders both became captivated by this book, causing the younger members of the family to all glance at it with wide eyes.

The head of the household had gathered family to greet the guest yet was engrossed in reading instead of leading them to honor the guest—a rather bizarre situation.

"…Hmm."

"…Umm."

"…Ahem."

In the customs of Zhongyuan, pointing this out would seriously harm the host's face.

From the guests' perspective, there isn't much to do apart from making noise to show their presence.

This miraculous gathering of guests was somewhat disrupted when Tang Lan-Ah dashed off to change her clothes, wondering why our Qing wasn't arriving, snapping all back to reality.

"No, what are you all doing now? Our Qing has arrived, what kind of welcoming is this?"

"Whoa." "Ahh."

In any case, the Tang Family of Sichuan!

With only a distance remaining until home being a total of an additional two thousand li, now reaching Chengdu!

