\chapter{On the Way Home (5)}

Qing's head tilted slightly.

Somehow, Ziyou's expression was peculiar.

The corners of his eyes were subtly downturned, his gaze was somewhat moist and greasy, and his lips were pursed pitifully as if he were deliberately pulling at the corners.

What was this, what on earth does that expression mean?

Ziyou cleared his throat with ahem, ahem.

"There is no need to be too discouraged. It is the nature of the country's affairs, and the fate that the bloodline of the Heavenly Dynasty was born with is a cruel one."

"Huh."

"They call a prince a King, but is there any other title in the world so hollow? Once a crown prince ascent the throne, the other imperial heirs are nothing more than a threat to the Dragon Throne, so they were merely exiled to a distant place with the title of 'prince'."

Ziyou smiled bitterly.

"Do you think a princess is any different? When the barbarians cause a ruckus, the country falls into turmoil and countless blood would shed, so it is more beneficial to send one person to quell it. This is not something the Emperor decides out of personal affection, so you are not chosen for such a role because you are particularly disliked."

It was a consolation that her father was not selling her off to the barbarians because he hated her.

That's just how princesses are, and it's not because you did anything wrong or were hated.

At that, Qing's head tilted even further.

Since Qing was not in a position to be consoled, what was this? What did it mean?

"And, in truth, the life of a princess in a peace marriage is not all that bad. Would those barbarians dare to mistreat a princess of the Heavenly Dynasty? Just as a prince is the master within his manor, the princesses of peace marriages also go and become masters. Their life is no different from the palace, no, it could even be said to be better than that stuffy Forbidden City."

People from Qing's hometown might argue, how could a political marriage without love, leaving the most advanced nation of the time to be married off as if sold to a barbarian tribe, not be bad?

But in this primitive ancient Zhongyuan, it was so rare to marry a loved one.

It was common for the bride and groom not to even know each other's faces before the wedding.

The reason men usually take concubines was because the main wife was a woman chosen by the family, so they take a lover they actually care for as a second wife or concubine.

And it's not as if the Forbidden City was a sweet home, a comfortable haven for the princesses either. In most cases, it was far from it.

At that, Qing nodded her head.

\textit{Hearing it, it might actually be a good thing for the fake Yuansui.}

But if there was one thing that bothered her?

"Uh, but is it okay to send a fake to the barbarians? If they find out, they might get angry, wouldn't they?"

"What is there to be found out? If the Heavenly Dynasty says she is a princess, then she is a princess."

In fact, it didn't matter if they sent a fake.

It was common to openly send fake princesses in the first place.

One. Call any maid from the palace.

Two. Adoption. From now on, she was the daughter of the Emperor, and bestow upon her the title of princess.

Three. Sell her off to the barbarians, and it's done!

The most famous woman among those who were transformed into a princess overnight and then sold off to the barbarians was Wang Zhaojun.

One of the Four Great Beauties of all time, the four most beautiful women from the past to the present, one of the Four Heavenly Kings of Beauty, Wang Zhaojun.

The process was also astounding.

The emperor of that time, Emperor Yuan, prepared for a peace marriage to appease the violent Xiongnu barbarians.

The fake princess was usually chosen from among the palace maids.

However, a palace maid was also a potential woman of the Emperor .

So, even for a peace marriage, he felt it was a waste to marry a palace maid off to a barbarian.

So he thought long and hard about which maid was the least valuable, who he could send without regret, and then clapped his hands.

'Yes, since she's a maid to be sent to the barbarians anyway, I should just send the ugliest one!'

Thus, he issued an Imperial Edict to have portraits of the palace maids drawn.

But?

The painter took money from the palace maids and added some touch-ups to their portraits.

Depending on the size of the bribe, the portrait became more beautiful, and if you paid extra, you could make someone else's portrait uglier.

The Emperor, who examined the portraits with these minor touch-ups, naturally had no choice but to pick the ugliest woman among them.

And so, after notifying the palace maid's family and going through the long process of entering her into the Heavenly Dynasty's genealogy, it was the moment when the Emperor and the new daughter met for the first and last time.

Wang Zhaojun. A super, super, super, super beauty.

According to records, the Emperor could not take his eyes off Wang Zhaojun's face and was completely captivated.

But what was decided could not be undone.

The Emperor was enraged and immediately issued another Imperial Edict to capture and torture the bastard who drew the portrait.

For the excessive touch-ups, the painter met a very, very gruesome end.

Meanwhile, the primitive tribal chief of the Xiongnu barbarians, Huhanye, had no expectations whatsoever about the princess that Zhongyuan was bestowing upon him.

She was a wife he would have to serve like a master, so he just hoped she at least looked human.

But then? The state of his wife?

The chief, Huhanye, having confirmed the beauty of his new wife, Wang Zhaojun, solemnly declared.

'As of today, the alliance with Zhongyuan was withdrawn.'

'The Zhongyuan and the Xiongnu will become one body.'

'Loyalty, loyalty! Your Majesty, may you live a long and prosperous life!'

So great was his gratitude that the Xiongnu tribe did not invade Zhongyuan thereafter, becoming a very loyal tributary state.

Wang Zhaojun also had a minor problem (the levirate marriage system; the Xiongnu had a custom where the son would inherit his father's wife after his death), which led to the tragedy of marrying her son after her husband died.

Fortunately, he was not her biological son, so she lived happily ever after anyway.

Furthermore, Wang Zhaojun was greatly revered as the mother of the Xiongnu, generously sharing the advanced technologies of Zhongyuan.

To the extent that a new law was created for Wang Zhaojun, making an exception for the biological mother when a son inherits his father's women.

"So, if you look at the anecdote of Wang Zhaojun, you will see that a peace marriage is not such a bad thing for a princess."

Qing's head tilted even further, now almost slanted to the side.

\textit{What is this? This voice? Why is oil dripping from his voice? Why is he pretending to be gentle?}

But Qing decided to let it slide for now.

\textit{Perhaps it is better for Princess Yuansui to go for the peace marriage. How comfortable could her position of living in the palace as a fake have been?}

\textit{Since I had never met her, how could I know if she had been living well in the Forbidden City, patting her stomach, or if she had been spending sleepless nights tormented by heartache?}

\textit{In any case, since she lived as a princess, she would have to accept the fate of a princess.}

\textit{Just about that much?}

\textit{She's a stranger anyway.}

\textit{There's no reason for me to care, right?}

"Hmm, well then, what."

"This one's words, ahem, are that I hope you are not too hurt."

At that, question marks, the symbols of her hometown, popped up above Qing's head.

\textit{What? The conclusion is weird?}

\textit{Is this a mood where I am supposed to be hurt?}

\textit{At what point am I supposed to be heartbroken?}

Only then did Qing understand Ziyou's expression.

It was pity, that kind of sorrowful tenderness!

"Wait. What is this? Why am I getting hurt? Is this a moment where I should be pitied? What is it? Am I being dense?"

"Hmm? Well, ahem, even if the princess going for the peace marriage is the fake Yuansui, for His Majesty the fake is the real one, right?"

"Huh. No? His Majesty knows too?"

Ziyou's expression became quite a sight to behold.

He looked exceptionally stupid.

"What does that mean?"

"Your tone."

"My tone is not what's important right now, what the heck is that,"

"Haven't you heard the rumor? That the young hero Ximen Qing visited the Forbidden City. I was found out there."

To Qing, the Emperor was a rather complicated opponent.

Before visiting the Forbidden City, he was a total bastard, and in terms of his actions, the Emperor was still a cold-blooded man without blood or tears, disqualified as a human being.

But even though he was such a bad guy, according to the ruling philosophy of this primitive ancient Zhongyuan, he was also a very diligent ruler.

That would be guaranteed by the number above his head, the karma of zero, with nothing above or below it.

Besides, considering what Princess Haryeon said.

He was actually a father who loved his daughter, but as stoic fathers always are, his expression of it was stingy and the method was wrong.

Also, a lonely head of the family misunderstood, a henpecked husband, a tired and weary office worker, hmm, since he's the Emperor, a CEO? A chairman? Except that his company was the entire Zhongyuan.

Qing's weakness was affection.

If you say you like her, she melted and immediately opened her heart, so the members of the Xue Family Trading Company, including the Great Demonic Adept Cui Liwen, with their high Evil Karma, were just welcome acquaintances to Qing.

The moment Princess Haryeon whispered, 'Dad was actually having a hard time too, and he loves you,' Qing's hostility softened.

Besides, seeing the Emperor's attitude, it seemed to be true.

And a part of her ego that cannot see herself as Yuansui, the big thorn of being a body snatcher, also arouses guilt towards him.

"So? What happened? With my brother's personality, he would never have tried to send you away, would he? Especially since you are involved in Wulin he despises."

"Uh, from what I heard, it wasn't for such an emotional reason, but more like, it's just work, so he have to kill all feelings? I thought he would have been a bit more human if he had been a bit more emotional."

At that, Ziyou lets out a cold sneer.

"Ha, human? Are you talking about my brother?"

"Hmm, but it seems like there is some if you look for it? But your tone keeps getting solemn, are we not friends? Should I use honorifics? I greet Your Highness? Your Hiiiighness, ten thousand years, ten thousand years, ten thousand ten thousand years. Have a veeeery Happy New Year!"

Qing prostrates herself with an exaggerated motion.

At that, Ziyou goes ahem.

"Ahem, hmm, this has become a habit. Since I keep using it, it keeps sticking to my mouth."

"That's all because you're not tense. Even between friends, you shouldn't be too relaxed and comfortable, you need to maintain a moderate amount of tension."

It was a statement that would have made Qing's friends utterly dumbfounded.

For someone who calls herself a friend, she shows all sorts of unsightly behavior, lying around and stuffing her face, a spectacle that only gets worse, so what tension was she talking about?

But Qing, a manly man who was always generous to herself.

It can happen between friends, what, don't best friends even fart in front of each other?

"Well, that's what happened. I am no longer officially Princess Yuansui. I am the martial artist Ximen Qing."

"That, umm, my brother would never have allowed that, given his personality?"

Qing flinched slightly.

In truth, Qing had made a secret backroom deal that she couldn't tell others about, to become the leader of Wulin Alliance within ten years and offer the Orthodox Wulin to the Imperial Family.

Of course, it wasn't to enjoy some kind of wealth and glory, but to buy time since Wulin was about to go up in flames.

Delaying it by ten years was a great achievement in itself.

\textit{But it was something I couldn't tell others.}

Qing said what she could say instead.

"Hmm, I did receive a government post instead, though. Inspector-General of the Twelve Bureaus? The atmosphere was such that I couldn't go home if I didn't accept it, so, well, that's what happened."

"The atmosphere was such that you couldn't go home……"

"It's true! The atmosphere was exactly like, 'if you don't accept this, you can't go', so I had no choice, what am I going to do as a high-ranking person."

"No, I am not blaming you. Just, hmm, yes, you have to go home."

Ziyou smiled faintly.

It's human nature to reveal one's inner thoughts unconsciously, and it seemed the Forbidden City was never home to his friend.

"But."

Qing said so and brought her wrists together, clapping her palms together twice in a peculiar clap.

"What is that? Is it perhaps a gesture used in the marketplace? I have not seen it during my secret excursions."

At that, Qing grinned a mischievous smile.

"The envelope, the envelope is opened~. You don't know? If you've received the New Year's bow, you have to give a hongbao. You're not going to receive New Year's blessings? I don't really need New Year's money or anything like that either, you know? I'm so rich. But this is all for a friend to receive blessings, so I'm specially giving it."