\chapter{On the Way Home (6)}

Ziyou quietly sorted his thoughts.

\textit{Not only did my brother release Yuansui, but he also granted her the official post of Inspector-General of the Twelve Provinces?}

Ziyou smirked crookedly.

Indeed, to a Crown Prince, his brothers were worse than strangers; it was to the point where one wondered if there had ever been a loving imperial family in history.

"Fox. His Majesty has granted my dear friend the rank of Inspector-General of the Twelve Provinces. What are your thoughts, can you fathom the Emperor's intentions?"

"To the Young Lady, you mean? Hmm."

Chuanglan Jinhu wore a worried expression.

Before dedicating himself to the King's Manor, Chuanglan Jinhu was truly the greatest swindler in the world.

Swindling requires a sharp mind, and he also served as the Manor's strategist.

Chuanglan Jinhu stroked his sly goat beard for a good while, then cleared his throat with ahem.

"Well, as I understand it, the Young Lady's martial talent is no ordinary thing. She is a martial artist considered to be the next Greatest Under Heaven, and not just the greatest, some say she will become a great master comparable to Celestial Martial Emperor."

\textit{I didn't realized Yuansui is so talented in martial arts .}

\textit{Then again, she was already a master when I last saw her, so perhaps she had become even more of a master now.}

"What if, after the Young Lady becomes the Greatest Under Heaven, His Majesty bestows upon her the rank of princess?"

At that, Ziyou's expression hardened.

Chuanglan Jinhu, observing Ziyou's complexion, quickly added.

"Of course, it is an extreme hypothetical. Celestial Martial Emperor has already caused so much havoc, so wouldn't it be rather difficult to make such a proposal to the Young Lady after she becomes such a master? However. She has already accepted the post of Inspector-General of the Twelve Provinces. Just by His Majesty widely proclaiming that fact to the world, he can make the Young Lady a member of the officialdom."

Ziyou's expression hardened further.

The idea of bestowing the rank of princess upon Yuansui again was not an extreme hypothetical, but practically a decided future where the pieces fit perfectly.

In other words, it meant the birth of a Celestial Martial Emperor belonging to the Imperial Family, no, belonging entirely to the Heavenly Dynasty.

The problem was that King Dexian's Manor had been subtly provoking the Imperial Family.

What if the Emperor had changed his mind from annihilating Wulin to subjugating it?

The original plan was to gently provoke the Imperial Family, and if the tip of the sword eventually turned towards them, they would resist together with Wulin forces.

They had already won over the Sichuan Tang Family, and it was clear that the Emperor's sword would be aimed not only at the prince's manor but also at Wulin.

They thought they could easily win over Wulin, having a common enemy for the sake of survival.

But if the Emperor retracted his grand policy of annihilating Wulin, the situation would become very tricky.

If it became a conflict between the Imperial Family and the King's Manor, not Wulin, would Wulin really want to get involved?

On the contrary, the Sichuan Tang Family would be the first to pull out.

Therefore, it was an unavoidable situation.

They had no choice but to lay low.

The act of calling the Sichuan Tang Family to receive New Year's greetings was also to provoke the Imperial Family, so this was a situation that needed to be resolved first.

"Your Highness, for now, please open the manor. If Your Highness announces that you will receive New Year's greetings from everyone, wouldn't the greetings from those Tang Family become a non-issue?"

This in itself would be a message to the Imperial Family, a declaration of surrender that said, 'On second thought, I think I crossed the line, so I'll cancel it, please spare me.'

However, if it was a word of blessing from the King from the start of the New Year, people from all over Sichuan would flock to them.

He would probably be reduced to receiving greetings all day long for the ten days until the Spring Festival ends.

Ziyou gave a bitter smile.

\textit{I had thought to share some friendship with a long-lost friend, but who would have known she would drop a bombshell like this.}

"Still, it is truly a stroke of heavenly luck that the Young Lady delivered the news. Hehe, isn't this a connection sent from the heavens?"

\textit{On the other hand, it is a great relief, if I hadn't known, I would have eventually faced the Imperial Family alone and met a miserable end.}

"Hmm."

Chuanglan Jinhu discreetly observed Ziyou's reaction.

Then, with a hehe, a shameless laugh like that of a sycophant, he slyly brought up a point.

"Your Highness, and there is an even better way. Hehe."

"What is it?"

"Before His Majesty wins over the young lady, Your Highness can do so first, can't you? What about a Celestial Martial Emperor of the King's Manor, not of the Imperial Family? That would be like gaining a thousand troops and ten thousand horses."

"Win her over, you say? Would that be possible? My friend is already a renowned master of Wulin. No matter how deep our friendship is, she would never lend her strength to the King's Manor. Also, His Majesty would do whatever it takes to prevent that."

Of course, on a personal level, that is, as a friend, she would come to save him if he was in danger, but that was as a friend, not to lend strength to the King's Manor.

At that, Changnan Geumho's voice became secretive.

"Hehe, we just need to create a situation that even His Majesty cannot do nothing about it, and if you form a bond that even His Majesty cannot sever, it will be fine. Your Highness."

Chuanglan Jinhu, beaming, continued.

"For example, how could His Majesty tear apart the bond of a couple already united in marriage?"

After saying so, Chuanglan Jinhu slyly raised his head and looked at the ceiling.

And his eyes met perfectly with the person on the crossbeam, Hag Yan, who met Changnan Geumho's gaze, quietly gave a thumbs-up.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Liaoning Province, in the dead of night in Heishan County, a middle-aged man with a blade at his side staggers across.

His appearance gives a hint of his martial prowess.

The very act of walking drunk on a dark, empty street in the dead of night was evidence of his confidence in being able to protect himself with his own skills.

People from Qing's hometown might say, what's so great about just walking on a night street while drunk.

Qing's hometown was a country that provided the safest nights in the world even in an era where the night had been conquered, so it was difficult for those people who do not fear the night to understand.

But in this ancient, primitive prehistoric age, the night was not yet conquered, and wasn't nighttime passage also forbidden by national law?

Besides, every martial artist carries grudges and favors, big and small, so wouldn't wandering around alone and drunk at night be the same as throwing down a challenge to one's enemies, saying, 'come kill me'?

Thus, one could easily guess that the middle-aged man was a master, at least one worthy of the title.

It must be a confidence in his own skills, a belief that says, 'come what may, be it an enemy or whatever.'

Of course, anyone becomes a dog when drunk, so one might retort, isn't he just a drunkard who can't tell heaven from earth?

In the ruthless Wulin, such a person would not live to see middle age; they would all be dead.

In reality, the middle-aged man was a master.

For he was the Heishan's Number One Master.

And according to the strict rules of Wulin titles, the number one master of a region had the honorable right to use the name of that region.

The middle-aged man was the Heishan's Number One Master-

"Heishan Saber Maogan, is that right?"

The staggering Maogan came to a halt.

Under the moonlight, a man suddenly stood there.

Two swords on his right, one saber on his left, and from behind his back jutted out large weapons like a spear, a greatsword, and a wolf-fang club.

"I don't know who you are, but I am pleasantly drunk for the New Year, so I would be grateful if you would return without spoiling my mood."

At that, the man smiled brightly.

"That's great. Isn't it a fine time to pleasantly share martial arts ? Don't be shy, let's have a proper discussions at it."

"You want to spar?"

"How can one's skills improve with mere sparring? Only a fight to the death raises a martial artist ."

A fight to the death, a life-and-death duel.

Simultaneously, ssssk, men in black emerged from the alleys of the street, forming a pincer formation in front and behind.

A sharp scent of alcohol immediately erupted from Maogan's entire body.

A moment later, Maogan, having completely shaken off the effects of the alcohol, gravely drew his blade.

"I need to know who I'm fighting."

"The Plunderer."

Maogan swallowed hard.

\textit{To think the Plunderer actually existed.}

\textit{I've run into a madman.}

The Plunderer, a reclusive, mysterious master spoken of in hushed tones like a legend.

A strange person who appears secretly to request a life-and-death duel, and as the price of victory, takes either one's martial arts or one's life.

Originally, martial arts were more precious than life.

If one offered their martial arts instead of their life after a defeat, wasn't it the code of a martial artist to be treated as a coward who offered their skills to live?

Thus, those who clashed with the Plunderer and protected their martial arts lost their lives, and those who did not, survived and were reluctant to tell others.

However, humans were creatures who cannot help but reveal secrets, and the past of having been defeated and offered up one's martial arts was not so heavy a matter as to be protected at the cost of one's life.

So a rumor spread in secret that such a madman existed, and he was called the Plunderer.

Finally, the two martial artists clashed.

In an identical stance as if reflected in a mirror, the blade rising like a crescent moon from behind the lower back clashes in the middle, its arc broken.

"Moon Shadow Blade!"

"It's not that rare a blade technique, is it? They say you're the best among the masters of the Moon Shadow Blade, I need to know how great an achievement I have made."

On a clear night, enhanced qi and enhanced qi clash, and shattered starlight scatters on the ground.

Clang, clang, clang, the heavy sound of blades clashing.

It was truly an even match, neck and neck, evenly matched, tit for tat, evenly poised; blade met blade, sometimes flowing and being deflected.

How much time had passed like that?

As if by agreement, the two martial artists retreated at the same time, creating distance, and a heavy silence descended upon the street again, as if nothing had happened.

And a moment later, Maogan opened his mouth.

"I have lost."

It was a sudden declaration of defeat.

Why would he suddenly declare defeat against an opponent who was clearly his equal?

Because it was a staged even match; the man had been one-sidedly matching Maogan's level.

"Life, or martial arts ? I already know the Moon Shadow Blade, do you have any other martial arts ? Ah, for reference, I don't accept Qi Cultivation manuals."

"I learned the Black Fang Hand as a life-saving ultimate technique ."

"I already know the Black Fang Hand too?"

"The Sangpyeong Steps-"

"I know that one too."

At that, a look of despair spread across Maogan's face.

The Plunderer clicked his tongue and shook his head.

"There's nothing to learn, so you'll have to pay with your life. You lot. It's training time."

The Plunderer said so and immediately turned and walked away, and as if waiting, the men in black launched themselves forward all at once.

As the Plunderer walked away so indifferently, a woman was already standing nonchalantly in front of him.

An endlessly cold, emotionless expression.

Soon, a cold voice flowed from the woman.

However, with a side of Goryeo pastry (yakgwa).

"Lord Sordemon, a messash from the Chairmun."

"Good grief. Either eat or talk, pick one. No, why are you always eating something?"

"Then, eating ish firsht."

"Eating comes first? No, why is a Jiangshi eating human food like that? Shouldn't you be eating something like human blood?"

"Thas na'ty. Tas'es bad."

The woman, with the expression of a cold city woman, vigorously and deliciously tore into the Goryeo pastry.

The Plunderer walked on, and the woman stood next to him, matching his steps, nom nom nom.

And, finally, she swallowed the last bite with a gulp.

"Lord Sword Demon, a message from the Chairman."

"Alright. What is it?"

"It is said that Princess Yuansui will be passing through Liaoning on her way to a peace marriage with the Jurchens. He says the princess must die."

"Kill the princess? Why, has the princess learned martial arts by any chance?"

"Do you think she has? Please say something that makes sense. I wish you would think a little."

"He want me to cut down a wench who doesn't even know martial arts ? I can't do that. Tell him to get someone else. I don't have time for such useless things."

"Lord Sword Demon, if it's a princess, wouldn't she be escorted by a master from the Imperial Palace? I wish you would think a little."

At that, the Plunderer, the Sword Demon, smiled.

"Ah. I see. They say all the martial arts of the world are sleeping in the Imperial Martial Library, right? Perhaps they've learned the Divine Arts of the Nine Sects. Then again, the Chairman would know my personality well."

"Then, I will take my leave."

It was a woman who intended to leave immediately after saying her piece.

The Sword Demon called out to her.

"Ah, wait."

"What is it?"

"I bought some dumplings to eat if I got hungry, but it's a bit much to eat them at bedtime now. You have them."

The Sword Demon casually tossed a bundle.

At that, the woman immediately popped a dumpling into her mouth, bowed her head, and with her feet together, leaped up and vanished.