\chapter{On the Way Home (3)}

Chengdu, the chengdu of Sichuan.

The former chengdu (城都) refer to a city where the administrative office of a province was located, while the latter Chengdu (成都) was the name of the city.

However, because they were pronounced the same way, a rather amusing situation could arise for those who were unaware of this fact.

'Hey, Sichuan Jin, where is the provincial capital (chengdu) of Sichuan?'

'Chengdu.'

'Right, chengdu.'

'Yeah, Chengdu.'

'So, I'm asking where the chengdu is?'

'I just told you it's Chengdu.'

'Yes, I just said chengdu, so where is it?

'I'm telling you. The provincial capital. Is. Chengdu.'

'Aish, you son of a…!'

In truth, the people of Sichuan know full well that the provincial capital was Chengdu, so such cases were likely just the Sichuan person messing with you, but anyway.

Currently, a grand feast was being held in Chengdu.

It wasn't a particularly unusual event.

Tonight was the night of New Year's Eve, a night where not just Chengdu but the entire Zhongyuan was bustling with New Year's festivals.

But Chengdu's New Year's festival was a little different from usual; this time, it wasn't just a festival but a grand festival!

Because the Sichuan Tang Clan had opened their coffers, bought out all the food from the street stalls and eateries, and was now giving it away for free.

Of course, high-end inns and teahouses were exceptions, but well, those with such financial means had no reason to seek out free things, nor would they be particularly grateful for receiving them.

But for the common folk, on a good day like this, snacks were a burden, their children were begging for food from the stalls, they craved a drink and wanted to share something with their family, but their pockets were so light that only coins rolled around…

At a time like this, suddenly, food and drinks were unlimited and free!

Of course, it was a characteristic of the Chinese people to cause a ruckus, a mess, a dog-eat-dog scene as if to pack away a whole year's worth of food whenever such a thing happened.

But you have to pick your fights, and in the land of Sichuan, no Sichuanese person dared to cause a scene at an event hosted by the Sichuan Tang Family .

Because such a Sichuanese person would already be a dead Sichuanese person, having been poisoned to death.

Anyway, the common folk, holding up their free drinks high, shout a toast in loud, resounding voices.

"We wish Heavenly Blossom Sword great fortune!"

"Great fortune!" "All the world's fortune!"

"Sichuan's Best Sword!"

"Sichuan's Best Sword?" "I like that! Sichuan's Best Sword!"

The free drinks and food were provided by the Sichuan Tang Clan , yet strangely, it was Heavenly Blossom Sword who received the thanks.

Why?

Because it was a New Year's grace bestowed by the Sichuan Tang Clan in accordance with the will of Master Heavenly Blossom Sword!

Sichuan Tang Clan , a massive Xie-en grand feast!

Xie-en (謝恩) means to repay with a heart that cherishes grace, a phrase merchants in Qing's hometown would sometimes use when holding discount events to thank their customers.

Of course, there was no grateful heart at all, far from repaying, the purpose was to make their own money, and the discount was a mystery, where the price of an item would suddenly rise and then be cut, making it unclear if it was cheap or the same.

But the great Sichuan Tang Clan was different from such petty people. Was it not the family motto of the Tang Clan to be great magnates when repaying a favor, and the pettiest of the petty, a micro-minimal-petty person, when repaying an enemy?

Although Qing was already a benefactor of the family, that matter had already been settled by delivering the Sichuan Tang Family 's Gratitude Token.

Of course, this wasn't just a single gratitude token.

Even the lowest-grade bronze token of the Sichuan Tang Family's gratitude tokens came with all sorts of minor benefits, and on a larger scale, it was a Sichuan Tang Family voucher that promised to help once, no questions asked.

And the highest-grade gratitude token that Qing received?

From this day forward, Heavenly Blossom Sword and the Sichuan Tang Family will be one body. An attack on Heavenly Blossom Sword was considered an attack on the Sichuan Tang Family .

It was practically an honorary Tang Family certification.

But then?

The honorary Tang Family member Qing, roughly Ximen Tang-Qing, brought the research books of the Blood Cult to the Tang Family.

Qing's thought was that since the Tang Family was the most expert in this area, they should research it and share it with the Martial Alliance .

But from the Tang Family's perspective?

This was a very clear sign of goodwill from Qing and an immense favor.

Even with the same data, the results obtained differ depending on who conducts the research.

The vast research records on the poisons used by the Blood Cult and their effects could be shared with Wulin Alliance in terms of research results on poisoning symptoms, diagnosis, and antidotes.

But at the same time.

It would allow them to elevate the Tang Family's existing poison arts to a higher level, and such aspects did not need to be shared, and indeed, were parts that should not be shared.

So, if it had been any other martial artist besides Qing, it would have been very difficult to think of entrusting this to the Sichuan Tang Family so readily, even if they were a family member of the Orthodox sects .

Or they would have tried to demand a considerable price.

But Qing just handed it over cheerfully and did not ask for any price or reward in return.

The emotion the Sichuan Tang Family felt at this could not be described with words.

So, how were they to repay this favor?

Money?

But Qing was not a person interested in gold and silver, and wasn't Divine Maiden Sect rumored to have become very wealthy these days?

The gratitude token had already been given, and moreover, Qing's gratitude token was of the highest grade.

There was nothing particular to give, but this immense gratitude had to be expressed.

Then, what could it be?

Honor! The hearts of the people!

And that was the reason why the people of Chengdu, for no reason of their own, got to enjoy an unprecedentedly prosperous New Year.

There was no way Qing would miss this grand feast.

The streets were lined with red lanterns that bring good fortune—red being the color most loved by the people of Zhongyuan as it symbolizes wealth—and red lanterns hang from disorderly clotheslines that randomly cross the streets, eerily illuminating the black night.

Beneath them, the excited common folk clash their brass bowls filled with zhuojiu\footnote{濁酒; unstrained rice wine}, drinking and shouting, 'Good fortune to Heavenly Blossom Sword!' 'Best Beauty in the World!' 'Sichuan's Best Sword!'

\textit{Hmm, but it feels a bit strange that my name was heard in every toast.}

\textit{And what's this about Sichuan's Best Sword? Why me?}

But regardless of time or place, the one who buys the food was always the best. To the common folk of Chengdu right now, Heavenly Blossom Sword was the best in Sichuan.

The children, excited by the rare free sweets, run around with candy and tanghulu clutched in both hands.

And in the well square, a giant lion with more than ten legs dances fluidly.

Surprisingly, the lion dancers were almost all volunteers.

They make it themselves, they practice themselves, and so they work up a sweat to play joyfully a few times a year, on New Year's Day or the Mid-Autumn Festival.

However, in most cases, the passion of the person in charge of the lion head far exceeds that of the rest of the body.

Usually, the head pranced about, while the body got dragged along, unable to hid its exhaustion.

If they were professional acrobats specializing in the lion dance, they would be running, flipping, and spinning, creating a ruckus, and that would be cool in its own way, while this was funny in its own way.

Ciyu's eyes, watching the slightly clumsy lion dance born of excessive passion, sparkled for the first time in a while.

"That, monster. It's a monster."

"Ahem. That's a lion. A lion."

"A lion? It's a lion?"

"It doesn't exactly look like a lion. But let's just say it's a lion."

At that, Zhuge Ihyun's eyes also sparkled.

"Sister? You mean you've seen a lion before?"

"Huh? You haven't seen a lion?"

"Where could one possibly see a lion? Isn't it a beast that lives in places like Bosi\footnote{波斯;Persia} or Tianzhu?"\footnote{Surprisingly, North African lion subspecies distribution range is as far as India}

"Ah. That's right."

\textit{Come to think of it, it's not like there were zoos in Zhongyuan.}

Actually, there was a zoo.

Over there in the Forbidden City.

But the Forbidden City zoo was a place that raises exotic animals presented to the Emperor, a sanctuary that one cannot visit just because one wants to.

"If you say it doesn't look like one, then what does it look like?"

"Hmm. Like a yellow tiger without stripes, but with a magnificent mane? Ah, that's only the male. The female was no different from a yellow tiger, right?"

A zoologist would have been quite disappointed to hear it, but Qing's knowledge of biology was at about this level.

\textit{Come to think of it, weren't tigers and lions animals that could interbreed?}

\textit{Hmm, what should I call it in the language of Zhongyuan, a hulangzhi? A shilang? Well, whatever}.\footnote{Although Qing mention Zhongyuan(Chinese) language, the pun only worked in Korean. Tiger is 호랑(horang), lion is 사자(sarang). Mixing it up we'll get 사랑 (sarang), which means love}

And so they wandered without a destination, eating, eating, eating, and eating; in truth, what purpose could there be in such a feast?

It's just the fun of people-watching and grabbing things to eat without a care in the world for once.

And as they did, at some point.

Fweeee…

A sharp sound from far away, but like the sound of a whistle that fades away faintly and quickly.

And soon after, Bang…! Ba-ba-ba-bang.

White, red, turquoise, and blue fireworks bloomed brilliantly as dots in the night sky.

Followed by fwee, fweeeeee, continuously soaring shells, and the sight of fireworks filling the sky.

Fireworks were a spectacular sight that even modern people accustomed to light pollution cannot take their eyes off, so how much more so in Zhongyuan where there was a lack of things to play with and see?

The people on the ground were mesmerized by the sight of the fireworks embroidering the night sky and look up.

It was a grand fireworks display announcing the end and beginning of a year.

\textit{Ah, another year has passed like this.}

\textit{So how many years have I been in Wulin?}

\textit{Seventh year? Wow, then it's almost the tenth year, rounding up makes it ten, so I've been in this primitive ancient Zhongyuan for almost ten years.}

\textit{Yes, it's already been ten years…}(not really)

\textit{Come to think of it, it was such a hardship when I first fell into this primitive era.}

"Qing'er, Happy New-" "Happy New Year-"

Tang Lan-Ah and Xue I-ri, who had spoken at the same time, look at each other with displeased expressions.

Ciyu was still in Jian Buxi's arms, and both of them, with their heads tilted back, were lost in the fireworks, dazed.

"Have a Happy New Year."

"You too, San, get your blessings, and maybe a little less luck with women."

"Sister, I wish you a Happy New Year."

"You too. Zhuge, you too."

As she exchanged New Year's greetings with her friends like this, something tickled inside her heart.

\textit{Hmm, all of this, hmm, I miss Master…}

The fireworks display continued.

And when the fireworks end, this feast would also come to a close.

Because the first day of the new year will be busy from the morning.

Now they have to sleep, wake up tomorrow morning to give New Year's greetings to the elders, have a meal for good fortune as the first meal of the year, and also offer ancestral rites to their ancestors.

And at some point.

The fireworks that had embroidered the sky stopped abruptly, and only the heavy smell of gunpowder that drifted down belatedly lingered in the surroundings.

It was the moment a year had completely passed.

Seventh year after Ximen Qing's debut in Wulin, begins.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

What was the start of the new year?

It's tteokguk!

Without tteokguk, it's not the new year!

But the tteokguk of Zhongyuan was unfortunately completely different from that of Qing's hometown. Nian gao, the tteokguk of Zhongyuan, was a thing where sweet items like honey-filled rice cakes or red bean paste-filled ones were plopped into a savory, rich meat broth.

\textit{To put it another way, honey tteokguk?}

\textit{This isn't, this isn't tteokguk!}

\textit{Sweet rice cakes in meat broth, food like this shouldn't exist! Food like this shouldn't exist in the world!}

\textit{Since this kind of tteokguk shouldn't exist, I have to get rid of it quickly.}

\textit{I can't waste food, so I have no choice but to eat and eliminate this terrible food-adjacent something.}

So Qing diligently cleared away the nian gao.

\textit{Sadly enough, the honey tteokguk is delicious.}

\textit{Something like this shouldn't be delicious, is the sweet and savory combination truly invincible…!}

And so, a spectacle of a woman clearing nian gao.

It was after a wave of wondrous gazes had passed through the Sichuan Tang Family's banquet hall.

After eating breakfast, the time that children wait for all year long, and the time that adults do not want, would follow.

It was time to collect New Year's hongbao\footnote{red envelope filled with money}.

So, after the breakfast table was cleared, it was a time of waiting for when to offer the greetings.

But?

The Tang Family Head was dismissing the family members.

"Hmm, the New Year's bows should be made after paying respects to the King, so you all should go take a New Year's bath for now. I will probably be back after lunch. Ah, Heavenly Blossom Sword, shouldn't you pay your respects to the King?"

"Ah. Right."

Qing finally remembered one person.

\textit{Come to think of it, Zhiyou lived in Chengdu.}