\chapter{On the Way Home (4)}

If a King's manor was established in a city, it was a natural annual event for the local dignitaries of the area to offer New Year's greetings.

But what if it's a major sect of Wulin?

Somehow, that image becomes a bit awkward, and even strange.

Kings were the Emperor's potential political enemies.

Martial sects were de facto military groups.

But for these two to join forces?

Wouldn't anyone see it as a dangerous picture?

Of course, the martial sects mentioned here refer to the Nine Great Sects, the Ten Great Families, or other large forces whose fame was widespread within a province.

Small martial arts academies that just take in training fees, or small sects that gain profit by collecting protection fees in a small area or monopolizing certain items, were not even considered martial sects in the first place.

That was because these small-time operators were closer to joining hands with the local law enforcement , calling each other brothers and helping each other out in a 'what's good is good' manner, far from the principle of non-aggression between officialdom and Wulin.

In that sense, the act of Sichuan Tang Family's main lineage offering New Year's greetings to the King's manor could, in itself, be a huge problem.

How could the Sichuan Tang Family be just a gathering of somewhat venomous, no, very venomous poison users?

It was tantamount to a great influential family, which projects its influence over the entire Sichuan region, shouting that it was pledging allegiance to the King.

If so, what on earth was the Sichuan Tang Clan thinking, offering greetings to the King's manor, and what ulterior motive did the Krince's manor have in accepting it?

Under the already unfavorable gaze of Beijing, were they throwing them something to be criticized for, a defiant provocation as if to say, 'So what are you going to do about it, try and take my head if you can'?

Of course, Qing didn't know the answer!

Never mind the answer, she didn't even know why it's a problem!

She had no thoughts, because that was who Ximen Qing is.

She just thought, if there's a King in the same city, it's natural to offer New Year's greetings.

Upon entering the King's manor, the Tang Clan Head , Tang Tujuk, and his eldest son, Tang Jincheol, left first, saying they would represent the Tang Clan in offering greetings.

In the spacious room, only Qing was left all alone.

Qing was a martial artist, but also a proud fledgling carpenter who can hold her own.

\textit{From a carpenter's point of view, this place felt less like a guest room and more like the inner chamber of the mistress of the house, specifically the residence of the official wife.}

\textit{Firstly, the location of the room and the space it occupies in the building suggest so, and also, the decorative items usually placed only in the main wife's room—like mandarin ducks, Albizia flowers, and butterfly patterns, oh, there's a phoenix too?}

\textit{Seeing the phoenix decoration, this place is indeed a palace.}

\textit{Since it's a palace, well, maybe they build guest rooms exclusively for women.}

-Madam, are you inside?

"Ah, yes. Please come in."

When the door opened, an elegantly aged, yet stern-looking old woman, with not a single strand of hair out of place, neatly combed back, revealed herself.

Surprisingly, her identity was the former Great Chakra Witch, who was once a great Demonic Adept, and currently the number one retainer of King Deokmyeon's manor, Hag Yan.

For reference, the current Chakra Witch was a terrible murderer, and not only the Chakra Witch but also the White Hand Witch, Mad Slaughter Witch, Black Killing Witch, Purple Lightning Witch, Asura Demon Sword, and Soul-Stealing Demonic Adept, a star of slaughter who had packed in all the horrific demonic arts, any one of which would be dreadful to have.

"Madam, have you been well during our long separation?"

"Hag Yan, it's been a while. What do you mean, Mama? We agreed not to use that title, so you don't have to be so formal."

"You are still my Madam. But why do you intend to greet the Prince in that state?"

"Huh. Is there a problem?"

"Actually, I anticipated this would happen. Girls."

As Hag Yan clapped her hands twice, a group of women came rushing in.

Judging by their attire, they seemed to be the maids of the prince's manor, and in their hands, they held combs, scented oils, various colored powders, brushes, and bristles…

Qing's expression became a little awkward.

"Uh, there's no need to go as far as makeup-"

"Ahem. Girls, escort her."

Of course, Qing also knew how to do makeup.

No, could she…?

The teachings of Ximen Surin, the Way of the Beauty, had included makeup application, so she had learned it, but come to think of it, when was the last time she had done it herself?

At some point, even Master had stopped launching precision strikes even when she roamed around bare-faced, so perhaps she had given up.

But makeup was a bit much.

First of all, she hates the feeling of something painted on her face.

This is, of course, a characteristic of a manly man.

A manly man's way was to, after washing his face, slap on a watery, quickly-drying, and oil-free cosmetic with a pat-pat sound, and that's it. (No.)

Sometimes, there were guys who apply a load of sunscreem to avoid the sun, and their balls should be ripped off. (Absolutely not.)

Because that's what a manly man is.

At this point, it's impossible to know what a manly man even is.

Is one only qualified to be a manly man if they neglect preventable skin aging just because it's bothersome and troublesome?

Because this kind of talk about being a manly man, or a real man, was self-justification to package and validate one's own laziness, it was truly the epitome of a petty person.

But Qing was originally a petty person.

She was the shameless personification of hypocrisy, who thinks 'I can do it, but others are not allowed', and even a cowardly murderer whose sword was faster than her words!

In front of such a terrifying great demoness, the ordinary maids of the prince's manor cannot keep their wits about them.

"Kyaaa, Madam, your skin is like, oh my goodness, like silk. This is your bare face, right? My goodness, wow, how can you be so beautiful?"

"Wow, this hair, really. Not a single split end, and even though it's so fine, you have so much of it, wow, I'm so envious."

The maids, having a close encounter with the most likely candidate for the Most Beautiful Under Heaven, fawned over her in every possible way.

Originally, servants were masters of flattery who live by it, sycophants who live for the purpose of seeing the corners of their master's mouth twitch into a smile.

But at this moment, there was not a single lie, only pure sincerity-

First, surprise, then reverence, then embarassment. And then a flash of challenging spirit and determination.

Because, the higher a woman's beauty, the more difficult the makeup is.

To put it bluntly, if a woman was plain, you can just apply powder, let it dry, apply more, let it dry, and repeat endlessly to create a layer of artificial leather, a mask of a beautiful woman, and be done with it.

But a beautiful woman's makeup, if even slightly overdone, became an act of damaging her original beauty.

But it was an equally rewarding challenge, a rare opportunity to enhance beauty by adding to it as if it were there and not there, and also for the maids themselves to raise the level of their makeup skills by a notch.

The maids huddled together in a circle and exchanged fierce opinions in whispers.

"How should we adorn her? We can't diminish even a single hair of this beauty."

"A clumsy job would be worse than not doing it at all. Should we kill the color tones as much as possible for now?"

"Let's save the lip line and tone down the nose bridge a bit."

"What about the eyes? Save them? Kill them? She's beautiful, but her eyes are a bit sharp, giving a strong impression, don't you think?"

Constantly killing and saving.

At a glance, it was a terrifying meeting where one could get slightly confused whether these were maids about to do makeup or butchers plotting treason.

And finally, the maids all turned their heads at once, their eyes somehow blazing.

Well, the world was a place where you were dyed by your surroundings; a group was bound to be colored by a certain atmosphere.

The servants were just as worried about their King, who had no interest in women even as he aged.

"Now, Madam, please close your eyes first."

\textit{Hmm. Something feels, a little scary.}

\textit{But somehow, if she says to close them, I must close them.}

A moment later.

"Wow, Madam, you are truly beautiful."

"My goodness, Xishi would weep and Chang'e would tear her clothes in jealousy!"

The maids, with their noses somehow held high in the air, have a praise session, fawning all over her.

Listening to this, she was suddenly reminded of her beloved Siliang and Lianshu, the disciples specializing in guarding the main gate of Divine Maiden Sect, who would proudly have their names on the list of the world's greatest sycophants.

\textit{Hmm, it's all praise, so it's actually a bit…}

But somehow, with their noses piercing the sky, looking clearly puffed up with pride, they lifted and moved a large silver-framed mirror.

It's not a gesture they've done just once or twice, but one maid supported the reflective surface as if to block it, and then stepped aside with a 'Ta-da!' flourish.

In the mirror, an unfamiliar beauty was reflected.

The makeup, applied as if it wasn't there, simply added a pleasant complexion to her fair skin, and her slightly flushed cheeks seemed to hold a shy excitement.

Her originally slightly pouting, truly stubborn-looking eyes were rounded and gentle.

Adding newly drawn eyebrows to those eyes created a pitifulness like that of a sorrowful woman, or perhaps it stirred a protective instinct that made one want to hug her unknowingly.

And yet, only her lips were painted red, giving her a femme fatale feel, limited to the lower half of her face.

\textit{It's really pretty.}

\textit{Every time I see it, I'm amazed, it's always thrilling, always new.}

\textit{Today it's newer, more thrilling, and hmm, it has an addictiveness that I can't take my eyes off.}

\textit{The problem is, this is me.}

\textit{What good is it if I'm pretty? The one I like should be the pretty one…}

As Qing gazed into the mirror, somehow very, very intense, sparkling, and expectant gazes fell upon her.

They were looking at Qing with great longing.

Qing sighed inwardly.

\textit{Well, the maids need to have some joy in their lives too. I don't feel like it, but I have no choice but to react.}

Qing opened her mouth, her voice deliberately trembling.

"Is this, really……, me……?"

Qing's acting skills were only excellent in front of villains, so the line was stiff and awkward, but perhaps because of that, it seemed like she was harboring disbelief at her own changed appearance.

In Qing's hometown, it was a common line, but in Zhongyuan, where such popular culture had not yet developed, it would be considered the highest praise.

At that, the maids stomped their feet silently, some children clenched their fists, and someone else raised both arms, expressing a great sense of accomplishment.

\textit{Hmm, if you guys are happy, that's all that matters…….}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ziyou has no reaction.

He just seems like a corpse… he shouldn't be.

"Excuse me?"

"Hut, ahem."

At that, Ziyou, who had been spacing out, finally regained focus in his eyes.

Qing chuckled, a laugh unfitting for the innocent and pure makeup she had on for once.

"Is the person in front of me the neighborhood idler Ziyou, or the King?"

"Ahem, I'll be Ziyou."

"Well then, Ziyou, Happy New Year. Right, give me the hongbao."

Looking at Qing shamelessly holding out her hand, Ziyou made a face of disbelief.

"Do you demand New Year's money between friends?"

"It's been a while, so you seem to have lost your touch, but that's not your tone, you know? And, I know you've prepared it, so if you hand it over obediently, there will be no bloodshed."

"Hmm."

Of course, he had prepared it.

Still, it was an occasion to offer New Year's greetings to a King, at least nominally. If he sent her away empty-handed, what would become of the manor's dignity?

But now that she was demanding it so brazenly, somehow he didn't feel like just giving it to her.

Qing had a knack for being annoying.

"Anyway, have you been well?"

"For someone asking how I've been, you haven't contacted me once all this time. Weren't you planning not to come this time either?"

"Well, I can't just go knocking on the King's manor gate, and I can't just jump over the wall at night, can I? If I am staying at the Tang Clan, the scholar-in-white Ziyou could have visited, couldn't he?"

What a shameless thing to say about something she had completely forgotten.

Of course, due to a personal compulsion, she didn't lie and say she knew it would happen.

After asking after each other for a while.

Suddenly, Ziyou's expression turned serious.

"You, hmm, listen without being shocked."

"Huh? What is it?"

At that, Ziyou hesitated, as if about to say something very difficult.

As Qing waited quietly without rushing him, Ziyou finally let out a deep sigh and opened his mouth.

"It will be announced soon, but Princess Yuansui is to be married for a peace treaty. It seems the Jurchen barbarians have a new tribal chief, his name, was it Nuerhaci\footnote{Father of Hong Taiji, who later become the first Emperor of Qing dynasty}? It seems his power was formidable."

The expression that a princess was to be married for a peace treaty is, in simple terms, that she was being married off to the barbarians.

However, 'married off' was just a nice way of putting it, in reality, it carries the nature of a tribute and a hostage sent to barbarians who were difficult or troublesome to deal with.

It's a way of saying, 'We'll take good care of you from now on, so don't get any funny ideas and behave.'

In other words, you can just think of it as being sold off.

At that, Qing let out a groan, "Umm."

A mix of pity appeared on Ziyou's expression.

However, Qing's 'umm' was just an 'umm' that came out because it was awkward to say anything.

\textit{What is this? Looks like the fake Yuansui is getting married.}

\textit{So what?}

\textit{Is that something I should be shocked about?}