\chapter{On the Way Home (1)}

The easiest route for returning home from the Diancang Sect, namely to the Divine Maiden, was to stop at Sichuan and take a boat.

And not only was it convenient, but it was also the fastest way.

Taking the Yangtze River from Sichuan leads directly to the doorway of home.

In fact, it seemed that the Xue Family Trading Company has established a dedicated dock, being recognized for their contributions in developing Zigui, leading to a direct route to the Xue Family Trading Company as soon as one boards the boat in Sichuan.

Moreover, the advantages of this return route were not just speed and comfort.

First, Sichuan has the Tang family, and there were documents to be delivered to the Tang family, so it was possible to drop them off on the way.

Above all, the most significant benefit was that one could also visit the two great sects of Shichuan, Qingcheng Sect and Emei Sect, for a tour around the Absolute Sword Wall.

…That was the plan.

Unfortunately, the crucial visit to the Absolute Sword Walls has utterly failed.

A significant situation has occurred where the Heavenly Martial Emperor has sulked.

It appears even the senior Heavenly Martial Emperor, being old, has sulked childishly.

Of course, it was often the case that the elderly tend to sulk even more, as human nature becomes rather juvenile as they age.

\textit{Hmm, however, no matter how I think about it, the manifestation of the Grand Emperor Wuqing created by my heart does not seem to align with the aspects of the Grand Emperor Wutian himself…}

\textit{It feels suspect that he keeps insisting he was the Grand Emperor Wuqing. If he was created by my heart, isn't it odd for him to know things I don't?}

\textit{Or was that just due to that strange, incomprehensible Formless Skill?}

\textit{It remains a mystery.}

\textit{Is there really no Immortal?}

\textit{If there were, wouldn't it feel like I'm no longer in a martial arts world, but something entirely different? Yet, is it possible that there were no Immortals in this mysterious ancient primordial Zhongyuan?}

\textit{Then, could there be an afterlife as well?}

\textit{For now, no matter how much I ponder, it's still something I cannot exactly grasp.}

\textit{There is only one way.}

\textit{I must directly break through Hwa-gyeong and evolve to see if the ascension truly exists.}

\textit{However, that is a matter for a distant future, so for now, I should just head home…}

Thus, having wrapped up the tumultuous events of the Diancang trip, Qing was now on her way back.

To her surprise, Ji Yun Zenren, who had come to see her off, carefully asked.

"Well, about that Hao Youhui you run."

There were also levels of club types in Zhongyuan. Peers Assembly\footnote{緣議會; Yuan Youhui} was the one that anyone can freely join to form new relationships. The slightly more difficult one to join was the Faction Association\footnote{傰友會; Beng Youhui}

The final level, with a more exclusive nature was the Good Companion Association\footnote{好友會; Hao Youhui}.

So Qing tilted his head in confusion.

\textit{Hao Youhui? Have I ever done such a thing?}

"Rumor has it, quite secretly, that? The Half-Sword Twin-Saber Association? Perhaps 'Half-Sword' refers to the Dao and 'Double-Saber' refer to Jian?"

"That's correct."

"Ah, who came up with that name? It's a name that any swordsman or bladesman would dread. I wouldn't want to be part of a group like that. Honestly, it's not something to boast about."

"Hmm."

"Well, this isn't a request, I just thought I'd ask if you're accepting new members."

"Oh. Do you want to join, Ji Yun Zhenren?"

"What would I do hanging out with kids? It's nice if the senior and junior members were close, but there's always a distinction in rank. From my perspective, it holds no benefits."

This isn't something typically said out loud.

Yet Qing had become accustomed to Ji Yun Zhenren's way of speaking and knew there was no malice behind it.

"Ahem, there's someone named Wu Liang from the main sect. Do you know him? Also known as the 'Yiming Yang\footnote{One-Cry Sheep}.'"

The famous Yiming Niao, or One-Cry Bird.

There was a saying by Han Fei mentioning a bird that wouldn't sing, leading to ridicule from everyone. But when it finally does sing, it shakes the heavens, surprising all.\footnote{一鳴驚人; Yi Ming Jing Ren; One cry scaring men. From 'Han Feizi', chapter 21}

It referred to a giant that hides and waits for the right moment.

Wu Liang from the Diancang Sect was also known for this title.

However, the reason for Ji Yun's sour expression was that it wasn't a compliment at all.

Wu Liang was known as a notorious slacker among the members Wulin Alliance combat team.

"I know of him, but I have yet to meet him. They say he didn't even come to the Dragon and Phoenix gathering, and I haven't run into him either in the alliance."

"Ahem. I thought maybe seeing peers would motivate him, so I sent him to Wulin Alliance. I knew he would end up like this. That guy has truly lost his mind, tsk tsk."

Ji Yun shook his head.

"That guy was quite lazy, which must be infuriating for me. It would be one thing if he had no talent, but he should at least grab a sword among peers who possess some enthusiasm. I hoped to bring him to the Half-Sword Double-Saber Association. Oh, it isn't a favor, but I was wondering if you could grab his hair and hang out later. I've been contemplating a sword technique lately, which differs from the Diancang's, so it might be possible to teach it to an outsider…"

While a 'favor' implies requesting someone to do something through a bribe, in truth, it was about asking for a particular task while offering some form of incentive.

And mentioning a different sword technique that was unlike that of Diancang suggests a potential opportunity for Qing to learn it.

So, it's not that it's not a 'favor'.

"Ah, the Half-Sword Double-Saber Association isn't like Hao Youhui. It's simply a training session, so anyone who desires to join was welcome."

"Of course."

Qing merely stated the facts.

However, Ji Yun understood it differently.

"In that case, at least pass this order to him. The Grand Master has commanded that he join the Half-Sword Double-Saber Association."

\textit{Anyway, I was planning to stop by my home before heading towards the distant Changbai Mountain in the far east.}

\textit{Since I would pass by Wulin Alliance, I could just drop off that message.}

\textit{However, would he not just become a ghost member?}

\textit{Just a moment, speaking of ghost members, where on earth is that Changbin? What on earth is he doing that we haven't spotted him?}

Thus, leaving behind the farewell of Ji Yun Zhenren.

\textit{At last, my Diancang journey ends. Time to head home.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

They were going to stop by Kunming to greet the Langzhong Daren, but they found out he had departed just after the blockade was lifted two days ago.

The lifting of the blockade meant the prescription had been completed, and it seemed he had left to find another patient.

\textit{Though a bit disappointing, well.}

\textit{If fate allows, I may meet him again.}

Thereafter, they headed northward from Kunming towards Sichuan.

While Yunnan was known for its exquisite scenery, there are, unfortunately, no notable sights along the Kunming-Sichuan highway.

Send they were bringing books and other materials, they naturally travelled by carriage and staying in cities when they appeared, while camping out in the wilderness when not.

Most of the time during the journey was spent training.

Originally, the members of the Half-Sword Dual Association were entirely fired up with training due to Qing's antics of grandstanding.

So it wouldn't be excessive to think that the elders of the Orthodox Wulin viewed the Half-Sword Double-Saber Association as a gathering of serious young martial artists that shed blood, sweats, and tears to achieve even greater heights.

Xue I-ri was originally the type who pours every moment into training besides time spent eating or sleeping.

Zhuge Lixian was known for either lifting weights or reading books whenever he had a moment to spare, a combination that was quite peculiar yet both were his hobbies.

Peng Daesan wander around, but he practices consistently.

Even the absent members possessed diligent personalities or were utterly crazy about training.

Sword Lunatic was a renowned swordsman obsessed with swords, and Gong Sun-Yaoyi was determined to walk the path of a swordsman for the rest of her life.

Murong Zhuji had humbly accepted her shortcomings and, after rejecting vain attachments to what she lacks, became a truly dedicated training enthusiast.

Even Qing, excluding a few rotten behaviors, was quite a diligent martial artist.

Sure, there's a scene where onlookers had their mind blown due to her foolish indulgence in gluttony, or how she revels in laying down and resting after eating too much.

Yet, even in spite of this, Qing's training time was surprisingly substantial.

\textit{After all, as the leader of the association, one should set a good example, and no matter how high one climbs, it was never enough…}

It is said that Tang Lan-ah worked hard on taking on the role of a delinquent member of the Half-Sword Dual Association

The activities of the delinquent member were roughly like this.

While training, someone would complain about boredom and ask to play, and when others were training, they deliberately spread out snacks and munch away, then asking to go to the market, pointing out that some people were gathered nearby, wanting to go see a mask changer or a performer, or saying that they want to go shopping for medicinal herbs, and so forth.

Of course, interrupting training was mainly singular to Qing, as Lan-Ah didn't care what the others did.

Yet today, our Lan-Ah has changed!

For today, rather than glancing at Qing, she has been diligently focused on reading.

The materials obtained from the ruins of Five Poisons Sect seemed unexpectedly more interesting than expected.

Indeed, what captivated Tang Lan-Ah was none other than the title of the timeless miracle left behind by the nameless villain from the Blood Cult: The Method of Overcoming the Limits of Poison Techniques.

It's a title that would intrigue anyone who has been on the path of poison.

However, the most shocking aspect was the content!

Instead of sealing or hoarding the poison in one's body, it proposed breaking it down into harmless components and distributing them across the entire body!

Of course, there was also the disadvantage of a slow reaction speed, as the poison had to be combined again in the body to be used.

However, the advantage gained once you become accustomed to it was especially remarkable, as the storage ability of toxic substances within the body elevates while ensuring one's safety.

Most importantly, once familiarized, one can even synthesize various forms of modified poisons!

As a direct descendant of the top poison family in Zhongyuan, Tang Lan-Ah immediately recognized the revolutionary potential of this method, making it only natural for her to focus intently on the text.

Thus, the rare sight of all members actively engaging in training could unfold.

But in Qing's hometown, there exists a bizarre phenomenon called the law of preservation of idiots.

If you observed an ant colony, they say that a portion of them do nothing but play around.

If all the playful ants were to be wiped out, what happens?

Among of the remaining ants that worked hard, some would turn and play around proportionate to the previous ratios.

This law extends beyond anthills.

In a workplace, there were those with bad tempers, malevolent dispositions, and poor social skills, the so-called idiots.

Should this idiot somehow vanish for some reason, a new idiot might emerge from among those left.

('There's no such thing in our workplace'. If you say that, then you should suspect yourself.)

This was the preservation law of idiots.

Similarly, while Tang Lan-Ah was diligently working towards opening a new horizon in poisonous techniques, meanwhile…

On one side, there appeared a bum resting her head on a beautiful maiden's thigh, casually sipping cold wine while watching others train.

That bum was none other than Ximen Qing, the Heavenly Blossom Sword.

For Qing had grasped a new enlightenment.

The so-called 'Letting Go!'

\textit{Yes, whatever pleases my heart.}

\textit{I'm so obsessed with Profound Realm that I honestly don't even know what to do these days.}

\textit{Why don't I let go of everything and do as I please at ease, just as the esteemed master Ji Yun suggested without any burden?}

"Here, Xiao-mei. Ahhh."

"Yum."

Qing chewed the snack handed by Yi-mei, wondering what it was.

\textit{Is it a sweet potato cake? It tasted somewhat familiar.}

"Me too. Me too."

"Okay, niece too."

Parents were said a mirror to their children.

Lying on the opposite thigh of Jian Buxi, Ciyu eagerly eat the cake like a baby bird.

From the perspective of those training earnestly in front, it was indeed a discouraging sight.

Of course, while it was behavior that Tang Lan-Ah had previously displayed, poison practitioners were also a fundamentally strange individuals by nature.

Yet with the very originator of this behavior now doing the same…

Eventually, Peng Daesan let out a deep voice after a long absence.

It was a low bass that sunk in with the weight of the moment.

"Why not have a spar instead?"

"Huh? No way. Even if I seem to be playing, this isn't just play. It's what Ji Yun Zhenren said is necessary to reach higher realm."

Hearing this, Ji Yun Zhenren would be shocked if he heard this remark.

'I told you to do as you please. When did I say to play without a care?'

It would be the difference between freedom and indulgence.

Had he known this would happen, even Ji Yun Zhenren wouldn't have bothered to give advice.

"…Are you certain?"

"Of course, San is still in Early-Stage Transcendent Realm, so I'm not sure, but true masters must have time to themselves. Ah, being a master is difficult."

The saying that 'If you can't talk, you won't be hated' was probably exactly like this.

But what can be done? If it felt unjust, you need to reach Harmony Realm.

So today, as Qing got closer to home.

About three thousand li remain until reaching Divine Maiden Sect.
