\chapter{Journey to Shenyang (3)}

Qing hadn't specifically set out knowing the barbarians' base location.

She only knew they came from the north and arrived a little past lunch.

In other words, they likely set out from somewhere north early in the morning, riding horses to arrive just after midday.

Would she really head north based on just that? If the direction was even slightly off, they could end up in the wrong place after half a day's ride.

And what if the barbarians had traveled for more than a day? Wouldn't it be reckless to charge in blindly?

But Qing had no such concerns!

Because she never overthought things.

The open plains meant any barbarian tents would be visible from afar, right?

But what if the barbarians had taken over a day to reach Jianping?

Would it really change anything?

If a man draws his sword, he must cut something. Since they'd already set out, they might as well go further.

This was just typical Qing.

It wasn't like she was on some urgent deadline either.

Fortunately just as the sun was about to touch the horizon, they spotted structures glowing red in sunset to the north.

With Qing's superhuman vision, spotting anomalies in such open terrain was hardly difficult.

The barbarians' tents were already half-dismantled and loaded onto carts, with the remaining half being frantically packed away.

Meaning they were preparing to flee tonight. If Qing hadn't pursued them immediately, she might never have found them.

This was why having a strong body spared the mind unnecessary trouble.

Even with no plan, brute force could yield good results.

Qing reined Lü Bu to a halt and observed the busy Mongol barbarians in the distance.

After a moment Murong Jun asked curiously.

"Beggar Sister? Ah, there are the barbarians! Are they trying to escape? Shouldn't we chase them down?"

"They're leaving on their own. Why bother?"

"But they're barbarians. What if they come back later? 'Pluck the grass and pull out the roots' right? We should uproot them now!"

"That only works if the roots are deep. If there's a bigger bandit group, maybe we'd clear them out."

Qing looked again at the distant barbarians.

The small ones were likely children and the hunched figures were probably elders.

Of course there were plenty of healthy-looking adults too. And where there were children and elders, there were bound to be women.

"Jun'er. Looks like mostly women and kids. Are you going to kill them all? Because they're barbarians?"

"Huh?! No, that doesn't seem right…"

"Then should we spare them? If we leave them alone, the women would bear more children who'll grow into barbarian bandits and raid again. Should we let the barbarians alive?"

"Uh… That's not okay either."

"So? Kill them? Women and children? Slaughter defenseless people who don't even know martial arts?"

"That's…"

Murong Jun faltered and unable to continue.

It was a truly difficult question, a puzzle with no answer.

Meanwhile Warrior Lu looked at Murong Jun, was was lost in thought, with a pleased smile.

There was a commotion arose in the barbarian camp, but soon few mounted figures emerged from the crowd, blocking the path.

But they didn't charge.

They just stood there watching.

Time passed quietly.

The sun, having reached the horizon, slowly sets below it.

They say the sun is brightest before it sets.

Sunset, the splendor of the setting sun.

The sky was turning red, and the shadows were growing longer, now stretching farther than three \textit{zhang} long.

The sky was now getting dark.

The mounted figures at the barbarian camp finally turned their horses away.

They melted into the shadows, disappearing among their people.

Soon after, torches flickered to life throughout the camp.

Of course, if they wanted to work at night, they needed to light fires.

Seeing this, Qing turned her horse.

"Let's go."

"Huh? Just like that?"

"What? Should we kill them all? Wipe them out? Slaughter them so thoroughly they can't even scream?"

"No, that's not it but… Shouldn't we at least warn them not to come back, or tell them they'll be spared just this once? Something like that?"

"It's not cool to say it out loud. Let's go. We'll camp for the night. Ah, damn."

Only now did Qing realize—

\textit{Come to think of it, I brought the kid along too, but it's so cold out here.}

\textit{It wouldn't be a problem if I slept outside for a day or so in the bitter cold, but now I'm worried about Jun'er.}

\textit{Well, the kid is at least at Changming's level. Maybe it'd be better to ride through the night and head toward a village.}

\textit{But turning back to Jianping now would be embarrassing.}

"Wow! Beggar Sister, are we camping? Sleeping outside? Pitching tents, building a fire, hunting for meat and grill it?!"

Murong Jun's eyes sparkled even in the dark.

Well, this reaction was just right.

"Hmm? Jun'er never camped before?"

"Well, this is my first time running away from home."

Naturally, it'd be more troublesome if the kid were a habitual runaway.

Qing chuckled at his excitement.

\textit{If it got too cold I could just hug him. He isn't some kid who doesn't know martial art, so camping for one night wouldn't be a problem.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Fortunately, Warrior Lu had prepared for camping.

Of course, since this was an approved runaway trip, the guard had come fully equipped.

In addition, the Mongol cavalry's gear also included camping supplies.

Qing's group had looted everything intact.

Tarpaulins, fur sleeping bags, iron pots, and provisions—flour, dried meat, mare's milk, salt, and spices.

Just throw it all together and boil them, how could it not taste good?

Plus Qing had her culinary instincts, her 'hand flavor'.

Her mixed stew was so legendary, even her friends praised it with 'How could this thing be so delicious?!'

Her friends were all (well, except one) pampered nobles with refined tastes, having grown eating expensive food.

It was a luxury product guaranteed by those friends!

"Wow, Beggar Sister, this is amazing! It looks like horse feed but tastes incredible!"

"Heh, that's the beauty of mixed stew. It's the joy of having something different on the outside and inside, something that looks the same when boiled, but always tastes different."

So, they ate to their heart's content,

Since it was night anyway, she decided to go to bed early, so she laid down a thick tarp and pitched a makeshift tent on top of it, just high enough to crawl into.

It's quite comfortable to be wrapped up in a fluffy sleeping bag like a caterpillar, and you'll feel warm.

\textit{But, umm, the sleeping bag smells a bit, which is a bit uncomfortable, but whatever.}

After a while—

"Hey, Beggar Sister. Are you asleep?"

\textit{Actually, well, I already expected it.}

\textit{It's his first time camping, it'd be strange if he fell asleep right away.}

"Yeah. Beggar Sister is sleeping."

There was a sound of a kid giggling.

"Umm, Beggar Sister just let the barbarians go. Why?"

"What's the big deal? They gave up first."

"Gave up?"

"Like how you surrender in snowballs fight. They lit torches knowing we were watching."

"That's surrender? How?"

"They knew we were watching, but they let their guard down and just went in. It was getting dark, so if they lit a torch, they'd be clearly visible, but still they light the fires. So, what they're saying is, 'We're powerless. We're not trying to pull some tricks. So, kill us or let us live, do as you please.'"

"Ah."

"So, if we just left, it's the same as saying 'We'll spare your life. Just don't ever set eyes on Zhongyuan again'. There's no need to say anything, right? They'd know we shown them mercy anyway. One action speaks louder than a thousand words."

"Ohhh…!"

An awed gasp.

In Murong Jun's mind, the statue of a beggar-like true chivalrous hero shone brightly in gold.

On the platform below, stone fragments crumbled and golden words were engraved.

Actions speak louder than words.

\textit{So cool! This is a real hero!}

Qing's idol status skyrocketed! Limit break!

Thus, Murong Jun's first monumental camping experience unfolded.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The following day.
 
\textit{For some reason, Jun'er became more talkative.}

\textit{Not that he'd ever been quiet.}

\textit{From our first meeting, wasn't he a Sex Fiend candidate who would say anything he wanted to say?}

\textit{Jun'er is an expert in eavesdropping, who would leak out stories he had overheard like a leaky sieve.}

\textit{But now he is unstoppable.}

Qing figured they'd grown closer.

Well, that's just how kids were.

Once they warm up, they never shut up.

And it was all nonsense.

There was a story of how Guard-so-and-so marrying some Cook-so-and-so, but then it went by without any context and it turned to a story of a big bird he saw.

Then he talked about his favorite foods, briefly praising last night's porridge hunting, and then said 'Next time we camp, let's go hunting. Or catch fishes and roast them whole…'

Murong Jung talked about the next camping as if it's a given.

Then suddenly the topic of horses came up, again.

"Did you know? The original Mongol horses weren't pretty. They had short legs, their neck twice as thick, and their heads  huge and fat."

Qing pictured it.

Hmm.

"Sounds cute."

"If you see it in person, they're really ugly."

"Originally, ugly animals are the cutest."

"……?"

Human beauty and animal 'prettiness' were on entirely different realms.

In her homeland, Qing was a bit ugly, so she had a soft spot for unfairly ugly creatures

Especially dogs and cats with squashed faces or tragic expressions.

\textit{Not that I could keep pets.}

\textit{Living alone made it impractical, and the ones I liked were always expensive…}

\textit{In that sense, Lü Bu is, umm…}

\textit{Although he is a handsome horse\footnote{美馬; Mei Ma}, I prefer the dopey-looking Wang Gungdung\footnote{King Butt}.}

"Anyway, Wangchao? I heard that back then, the Mongolian barbarians saw Zhingyan horses and brought it here to use…"

王朝 (wangchao) referred to the fallen dynasty, the Yuan Dynasty, when Zhongyuan were conquered and ruled by the Mongols.

Mostly pointless trivia.

Originally, Mongol horses were formidable on northern plateaus, as they were strong, tireless, and cold-resistant.

But short legs made them slow, and they couldn't handle southern heat.

Their stubby ugly frames, who didn't suit the image of conqueror, didn't help either.

After conquering lands from Zhongyuan to the westernmots regions, the Mongols stole all wprld's famous horses and bred them.

It is said that there were no horses as excellent as the one ridden by the Mongolian barbarians these days.

"That's why, I think they want to run a little too. Horses, especially warhorses, need to run once in a while to avoid getting sick."

\textit{No, what does this mean?}

\textit{Isn't that exactly the same as saying that you have to start the car every once in a while to avoid it breaking down?}

\textit{Wasn't that just a myth?}

\textit{Or how people need regular beatings to stay fit, wait, no, that last one might be true.}

"Jun'er, we should ask the horse—"

"Beggar Sister, let's race! Giddyup!"

Before she could stop him, Murong Jun kicked his horse and shot ahead.

It was something that should have been done while holding hands and leading the way, but to just ride off on a horse by yourself and run away is the limit of a little kid.

After that, Warrior Lu's horse followed and run straight away.

Lü Bu whinnied and puffed excitedly.

He was clearly eager to run.

\textit{No, shouldn't you listen to my opinion too?}

\textit{I'm not really that fond with horses.}

Truthfully Qing's horsemanship was terrible.

Technology developed to compensate for human's weaknesses.

Because the fists were weak, people wielded weapons, and because the bodies were frail, people developed Qi cultivation.

On the other hand, overwhelming strength made techniques unnecessary.

Because of this, Qing's horsemanship cannot go beyond the level of simply relying on exceptional physical abilities that transcend human capabilities.

\textit{To begin with, horses are uncomfortable to ride…}

Qing sighed deeply at that.

"Fine, let's go."

\textit{First of all, it seems like I should take our secret friend home and send him to the Moyong family in Shenyang.}