\chapter{Journey to Shenyang (1)}

The Mongolian warrior pinned under the horse had a pale complexion.

Horses were naturally large and heavy beasts.

Only his shoulders were visible above the dying animal. Perhaps his ribs have already collapsed.

\textit{A warrior who once rode proudly across the land now lay crushed beneath his own steed. Well, I guess it's a fitting end.}

Then with a cough, the warrior spat out a mouthful of blood, his focus returning.

His eyes met Qing's as he looked up and he flashed her a smile devoid of malice.

"[Truly, your martial prowess is extraordinary, warrior. I salute you.]"

"[Still got time for small talk?]"

"[You will undoubtedly become a renowned warrior across the land. To fall to such a warrior is no regret. Though I must admit this is rather inconvenient. Could you finish me off?]"

Qing snorted in amusement.

\textit{Just moments ago, he charged at me like I was his sworn enemy, but now that death is near, he's acting all chummy?}

\textit{Is he afraid of not dying with grace, or is this some ploy to find an opening and survive?}

"[Before that. You were happily taking tribute from them, why suddenly decide to slaughter everyone?]"

"[What a strange question. Does a master need to explain why he slaughters his own livestock?]"

"[Huh.]"

He genuinely didn't seem to understand, so Qing just sighed and let it go.

She hadn't even questioned why they had to attack Jianping in the first place.

"[What was it, Great Warrior? If the Great Warrior orders you to die, do you just obey without question?]"

"[If there is a reason for the order, then there is no reason not to obey.]"

"[You'd die just because you were told to?]"

"[Hah, cough, wheeze, you are a warrior fit to conquer the world, but alas, you are still a Zhongyuan person. What warrior in this world would follow a leader who kills his own brothers without reason? If the Great Warrior orders death, there must be a just cause.]"

Qing pressed her lips together.

\textit{Well, if you just say 'just a Zhongyuan native who wouldn't understand', then I have nothing to say.}

\textit{If someone told him 'Go kill them' and he just replied 'Understood' without questioning it, how is that any different from a trained hunting dog?}

\textit{Actually, it isn't different at all.}

\textit{He is just a beast.}

\textit{A real person would at least question whether the order is right or wrong.}

\textit{Armed with independent thought, an independent warrior, umm, that doesn't sound quite right.}

Qing planted the zhanmadao into the ground.

There happened to be a Mongolian warrior's head between the sword and the ground.

Wasn't it the fault of the owner of the head who placed his precious head in such a dangerous position?

She walked around stabbing the zhanmadao into the ground.

Fools who couldn't even protect their own heads kept placing them in hazardous locations and suffering the consequences.

Meanwhile, Murong Jun, the genius of the Murong Clan.

Simultaneously Murong Jun was also an expert eavesdropper, the 'daytime bird and nighttime mouse' of the Murong Clan so to speak.

And to eavesdrop well one must first excel at hiding.

Thus an eavesdropping expert was in essence also a stealth expert.

Did Warrior Lu come out to help Qing for no reason?

No, it was an act of faith rooted in the unshakable belief that the young master would hide himself well and remain undetected!

So tucked away in a corner of the square—

Murong Jun had rearranged some furniture to create a blind spot and crouched behind it, watching the chaos unfolded.

He even poked a hole in the wall to get a clear view of the Beggar Sister's one-sided beatdown of the barbarians.

Qing's brawl was a masterclass in creative violence, unrestrained by martial arts or techniques, a primal freeform fight.

No, a fight can only be considered a fight if the opponent was on equal level. It was one-sided violence, sheer raw brutality.

And Murong Jun's reaction to this brutality?

"Beggar Sister is crazy! So cool!"

His eyes sparkled with admiration.

Ah so this was what 'cool' meant.

The strict, dignified sparring sessions with the Family Elders were nothing more than staged performances compared to this visceral display of violence.

Originally, Murong Jun's ideal warrior was his father, Murong Chengyi.

Dignified and serious, yet generous and unpretentious, the epitome of a noble hero, his martial arts exuding elegance and discipline, the kind of exemplary chivalry that only appeared in stories.

But now that ideal seemed to fade into a blur.

Overlapping with it was another image—

A disheveled beggar woman, playful and irreverent, utterly indifferent to others' opinions.

Yet in battle she became the most savage, more ferocious than anyone else in the world.

A seismic shift in the boy's definition of 'cool; was underway!

Qing was causing irreparable damage to his emotional development and moral compass!

Just how harmful was her existence? This was exactly why parents warned their children about bad influences.

Truly terrifying.

So once the battle ended, Murong Jun wanted to rush out immediately.

But before rushing out, he had promised Warrior Lu to wait at least an hour after any fight to assess the situation.

Still, the obedient Murong Jun waited before finally sprinting toward his amazing Beggar Sister.

And what was the amazing Beggar Sister doing?

Finishing off the remaining stragglers when—prrrrt!

She turned at the sound of a horse's distinctive whine, it was the black steed the barbarian leader had ridden.

Horses were already majestic creatures, but this one was exceptionally handsome.

As Qing stared, clip-clop clip-clop—

The black horse approached leisurely, its head held high before nuzzling her arm with its muzzle.

Qing absentmindedly stroked its neck, and it let out a pleased rumble.

Is this… flirting?

Did horses have the discernment to pick their owners? And right after its previous owner died?

Is it looking for a new master already?

A pragmatic thought perhaps, but it was the epitome of a quick rebound, with no integrity, loyalty, or righteousness.

"Wow, Beggar Sister, you got yourself a fine steed!"

"Huh?"

Murong Jun, who had been hiding somewhere, emerged after the battle and marveled at the black horse.

He reached out to pet it—

Snap! The horse's teeth clashed violently.

Murong Jun, whon yanked his hand back just in time, was unable to hide his disappointment.

"It must have decided to serve Beggar Sister as its master. It's really aggressive…"

"Huh? What did I do?"

"There are horses like this, what should I call them? Ones that like to show off? Leader horses?"

Some particularly intelligent horses understood the status of their riders. If they carried someone important, they'd strut around proudly reveling in the prestige.

And some took it further, refusing to let anyone of lower status ride them, as if offended by the mere idea.

"So it came to me because I'm strong?"

Is that… acceptable?

Weren't there famous horses known for dying alongside their masters? What was it? Red Hare?

The correct answer was Wuqi, the steed of the ancient warrior Xiang Yu.

But the only horse Qing knew was Red Hare.

"Aren't you going to name it?"

"A name? Well its old owner's dead so there's no way to ask… Hmm."

Qing studied the horse.

\textit{Let's see it's black so…}

\textit{Blackie? Kuro? Black Bean? Black Rice? What else was black? Oh jajangmyeon? I want jajangmyeon…}

If the horse could read her mind, it would have kicked her and bolted immediately.

But Qing was lost in nostalgia, yearning for the deep savory sweetness of her homeland's traditional dish.

After swallowing her saliva twice—

\textit{Wait, what was I thinking about again?}

\textit{Ah, the horse's name.}

"Alright. From now on, your name was Lü Bu."

"Lü Bu? Ooh! Like 'Lü Bu among men Red Hare among horses'\footnote{人中有呂布，馬中有赤菟; Ren Zhong You Lu Bu, Ma Zhong You Chi Tu}, the strongest steed right?"

"Nope. Because betrayal comes naturally to him. His last owner just died and he immediately switched sides to me."

"……Then why not Red Hare? Since it's black, call it Black Hare?"

"Red Hare? Doesn't Red Hare sound loyal?"

"Even Red Hare kept changing owners."

"Huh? Is that so?"

\textit{Come to think of it, Red Hare originally belonged to Dong Zhuo, then Lü Bu took it, Cao Cao stole it, Guan Yu received it as a gift, and Sun Quan snatched it away.}

\textit{What? I thought Red Hare was some legendary steed but it's just a symbol of betrayal.}

\textit{Well, anyone would covet a good horse.}

\textit{It's not like the horse could starve itself\footnote{Legend said Red Hare starved itself after Guan Yu died and Sun Quan took it}, or commit suicide by drowning its head in a feed bucket.}

Qing gently stroked Lü Bu's mane.

The texture was oddly addictive. Stiff yet soft, coarse like dog hair yet velvety like silk.

She kept petting it.

Warrior Lu was naturally taciturn, so he simply stood by Murong Jun's side.

Murong Jun looked at the horse enviously then, then at Qing, then glanced around.

"Beggar Sister?"

"Yeah?"

"Uh, are we just staying here? Watching you fight I felt like I understood something… but not really?"

"Hmm. Sparring would be nice, but let's do that later."

"Okay…"

Murong Jun deflated, but soon grew restless again looking around.

Still a child at heart, he couldn't stand being idle for long.

Kids have the hardest time enduring boredom after all.

But Qing wasn't just petting the horse to pass the time.

A short while later, thanks to the surroundings that grew quiet, the people of Jianping cautiously returned to the square.

Some gasped in shock. others gagged at the gruesome scene and fled to the corners.

But most cast fearful glances at the beggar who had caused this carnage.

As Qing silently observed them, Zhang Dae-in stepped forward.

"Great Hero, we are eternally grateful for your mercy."

"Great Hero? I'm no hero. Who said I am a hero? I don't do heroics. More importantly, what did I tell you to call me?"

"…Grand Supreme Beggar."

Qing studied him and her playful tone gone, her voice serious.

"You should leave this city. W drove off the barbarians for now, but more could come at any time."

"But Grand Supreme Beggar, this is our home, our lives. Where would we go?"

"That's for you to decide. Stay if you want. But do you think the next barbarians will be as lenient as these were?"

Qing scanned the crowd.

In fact, her revenge on Jianping was already complete.

She had only stayed to watch the barbarians before leaving.

Now that the show was over, she could leave anytime.

But no matter how much she disliked these people, she at least wanted to warn them before going.