\chapter{Journey to Shenyang (6)}

Southern foothills of the Khingan Mountain Range.

Three riders journeyed eastward along the valley of a mountain range, where towering ridges rose on either side, and cool streams stretched beneath the shade of lush trees.

The Khingan Mountain Range extended toward the vast Mongolian Plateau in the northwest, and sloped toward the Liaoning plains in the southeast.

So, the path east continued downhill.

A veiled woman deftly tossed ingredients into a pot.

A boy clinged to her side, chattering nonstop, his eyes sparkling like stars as he gazed into the pot.

Though the contents were thick brown and topped with a layer of yellow oil, hardly look like human food, it didn't seem to bother him.

Occasionally, when they reached open flat terrain, the horses were urged into a race.

Though 'race' was a generous term. It mostly involved the black horse charging ahead while the other two struggled to keep up.

When the woman on the black horse clutched her waist and groaned like an old grandmother before slumping to the ground, the black horse lifted its head proudly and let out a cheerful whinny.

The boy excitedly pointed out a pheasant.

Drool immediately dripped from the woman's mouth, and she pulled out a Mongolian bow tied to the horse, showing it to the boy.

Stars reappear in his eyes as they both laughed brightly and dashed into the forest together.

The remaining man left with the three horses leaned against a tree with his arms crossed, smiling contentedly.

Some time later.

The woman returned, carrying a massive wild boar slung over her shoulders, its front and hind legs gripped firmly in her hands. The boy, buzzing with excitement, followed beside her.

The man thought to himself, 'What happened to the pheasant?'

A feast was held in a small, nameless village they passed by along the way.

A wild board feast, to be precise. A feast held by the travelers who hunted a massive boar, weighing nearly 500 pounds, and generously shared with the villagers.

From Chaoyang County, 100 \textit{li} east.

From Beipiao County, another 200 \textit{li} east.

Though the 300 \textit{li} journey had taken two days with distractions, they make remarkably quick progress.

And so they arrive in Fuxin County!

Fuxin County was a military stronghold, home to the nation's horse pastures and two thousand-household garrisons for northern defense.

In other words. the military alone was 2200 troops plus their families, making for a sizable population.

If there was anything special, it was Taoist temples of the Wudang Sect—

\textit{Huh? Wudang Sect? Out here in the frontier?}

Well, it was Wudang and not Wudang.

Zhongyuan were vast, and ancient communication methods couldn't cover every corner, so local folk beliefs often took root.

It was definitely not the mainstream, but it was a slightly different kind of religion. Similar but not the same, in Zhongyuan language it was called 似而非信仰 (pseudo-religion).

Even in Zigui County, where Qing's house and Divine Maiden Sect were located, a strange indigenous belief was at its peak, where the Great Sun Buddha was worshipped, but somehow the Great Sun Buddha was in the form of a woman.

These weren't the mainstream Wudang Sect, but rather folk temples worshiping Zhang Sanfeng, Wudang's founder, as a deity.

Why?

Because this was said to be the hometown of Zhang Sanfeng himself!

"Ah, the revered Zhang Sanfeng…"

Not that it's worth sightseeing.

These weren't tourist attractions, but local temples for devout residents.

And military cities like this with their garrisons weren't exactly hotspots for travelers anyway.

So they plan to stay just one night and leave.

After a quick dinner, a scalding bath, and a table full of snacks—

Qing ordered another round.

"Beggar Sister, you're eating again…?"

"Why not? We've got nothing else to do."

"Uh, normal people don't eat snacks just because they're bored."

"That's the limit of ordinary person. Someone like me is different. Eating snacks then eating more, that's who I am."

"Whoa."

Murong Jun's expression shifted as if he's had a profound realization.

About 450 \textit{li} remain to Shenyang.

To the east of Fuxin County lies Mount Ta a slender towering ridge stretching vertically.

The fastest route to Shenyang on horseback was to detour north oh Mount Ta.

Because on mountain paths, horses and people moved at similar speeds, and some terrain was outright impassable for horses.

nevertheless, Qing insisted on climbing Mount Ta.

Why? Because her journeys were always straight lines, and when there was no path, she cut through obstacles with sheer physical prowess?

Not quite. Murong Jun suggested visiting the summit for the view.

And so the summit of Mount Ta.

"Whoa."

Qing gasped at the endless plains stretching eastward.

Liaoning's terrain was divided diagonally into three parts, flanked by mountain ranges on either side with vast plains in between.

To the southeast, the Changbai Mountains blocked the Korean Peninsula, while to the northwest, the Greater Khingan Mountains formed the border with Mongolia.

Mount Ta marked the eastern end of the Greater Khing'an range, boasting a breathtaking view of the Liaodong Plains.

On a clear autumn day, if you stood on its summit and had sharp eyesight, one could even spot the dark silhouette of the Changbai Mountains on the horizon and the distant city of Shenyang.

Unfortunately, during this time of the year, yellow dust blown in from the Mongolian deserts obscured the view even for Qing's keen eyes.

Four hundred \textit{li} from Mount Ta's summit.

The endless flat plains were perfect terrain for horses to gallop on.

At the halfway point to Shenyang, 200 \textit{li} in, lie Zhangwu County, a good place to rest for the night.

They set out after breakfast the next morning, arriving in Shenyang by midday at a leisurely pace.

And so Shenyang!

One of the ancient capitals of Zhongyuan with over 2000 years of history, Shenyang had long been the largest city in the northeast.

Once a thriving hub for Goryeo merchants facilitating Zhongyuan culture, its golden age had faded under later dynasties.

However it remained the most prosperous city in the northeast, bustling with Joseon merchants, Jurchen traders, and even the blue-eye-apparition\footnote{青目鬼} and Luxiya\footnote{露西亞; Russia} merchants from beyond the Jurchen.

It was a very strange sight to Qing.

\textit{Despite being unmistakably an ancient Zhongyuan city, the occasional Westerners stand out starkly.}

\textit{And hearing them speak fluent Zhongyuan language, I felt some strange dissonance.}

\textit{By the way, their noses really are something.}

\textit{No wonder they're called 'nose people'.\footnote{코쟁이; kojaengi; slur for Westerner, literally 'nose laborer'}}

At the southeastern edge of Shenyang, a grand estate's imposing gate finally comes into view at the end of a long avenue.

The sign hanging above it had four large letters written in flowing handwriting.

"Under Heaven Murong Family!"

The headquarters of the Murong Family.

As they approach on horseback, the gatekeeper bowed deeply with welcoming smile.

"You've returned, Young Master? How was your runaway adventure? It must have been tough leaving home. It's always sad to leave home. How far did you go?"

"Jianping? I even saw Mongol barbarians!"

"Haiyaa, it's best to avoid those savages. Though with Warrior Lu guarding you, I'm sure it was fine. And who might this young lady be?"

"Ah, this is Beggar Sis—"

"My name is Ximen Qing. Although it was too much of a title, I'm also known as the Heavenly Blossom Sword."

Qing cut off the 'Beggar Sister' remark with a dignified introduction.

The guard was also startled, then politely raised his hand in a proper posture.

"My apologies! I am Namryeong Mihak of the outer court! It's an honor to meet the Dragon of Wulin! I'll inform the Chief Steward at once. Seongchu, escort our distinguished guest to the main hall—"

"Ah, I'll handle it."

"Ah, Young Master will? Understood, I'll step aside."

\textit{Judging by the way he treated Murong Jun, it's clear he's the beloved young master of the family.}

\textit{Well, the child is abit unruly, but he's kind at heart…}

"That's the Oyak Pavilion. My great-great-great-grandfather loved crows so it's named after them. Now it's the inner court guards' quarters. Next to it was the Hohodang where the inner court guards train. Then there's the Hoban Pavilion the inner court dining hall—they always have piles of Shenyang-style chicken. Oh do you know Shenyang-style chicken? It's delicious. There's also Juhyeok a squad leader in the inner court. The guards were terrified of him but he is very tolerant with the dining hall Sister. Last time I even saw him getting dragged by the ear—"

Qing listened with one ear in and one ear out as Murong Jun barely paused.

“Oh, but sometimes, it seems like Leader Joo-hyuk got angry too. Last time, the two of them went into the basement, and I could hear dining hall Sister crying, but when they came out they were holding hands and laughing. Oh right in the basement—”

"Wait, Jun'er. Did you tell anyone about that just now?"

"Huh? Well Father, Uncle Musa, Squad Leader Yang…"

Murong Jun counted on his fingers, but for some reason, even after closing all of his fingers, he didn't stop and opened them again, continuing to count unfamiliar names.

Qing nodded.

\textit{Well, it must be a secret love affair that wasn't really a secret.}

Just then—

"Young Lady Ximen!"

The sound of feet kicking the ground, accompanied by a heartbreaking cry, rapidly approaches.

As she turned her head, Qing saw a familiar figure flying toward her with qinggong. A slender waist cinched tightly by a sash bending at an impressive angle.

It's none other than Golden Sun Sword Flower, one of the Five Flowers of Wulin embodying fairness, Murong Zhuji.

True to her character, she stopped shyly in front of Qing, gauging her reaction.

\textit{There's something endearingly timid about her like a small trembling animal.}

\textit{It's hard not to tease her.}

Qing narrowed her eyes and Murong Zhuji fidgeted with her fingers.

It was so aesthetically pleasing for a while.

Qing suddenly spread her arms wide and Murong Zhuji crashed into her embrace, her petite frame radiating a sweet peach-like fragrance.

"Young Lady Murong, how have you been?"

"Y-Yes! And you, Young Lady Ximen?"

"Oh just living my best life every day. I was on my way to Changbai Mountains when I found Jun'er running away, so I decided to escort him home."

"Ah, Jun'er."

"Sister, I'm back. Hehe."

"Welcome back! Are you hurt?"

"Nope! It was fun. We camped, went hunting, even caught a wild boar. Sister, have you ever hunted boar? We hung it up, slit its throat, roasted the snout, and then and then…"

\textit{Looking at them side by side, they do look like siblings.}

\textit{Jun'er's future likely holds a dashingly handsome man, though his height might be a slight disappointment. Still, with a face like that it balances out.}

"…Oh right! I even fought Mongol barbarians! I took down one and hid, but Beggar Sister killed like over thirty just spinning around—"

"Wait."

Murong Zhuji's face stiffened.

Well, what older sister wouldn't worry hearing her little brother fought barbarians?

With a stern yet concerned expression Murong Zhuji turned to Qing.

"Over thirty? Lady Ximen, were you hurt? Mongol bandits are known for their martial arts, but they're also cunning. You never dodge arrows, don't you? Mongol bandits use archery. You didn't know right? Of course you didn't. Did you get hit anywhere?"

She starts patting Qing down.

\textit{Hmm. So that's her concern.}

\textit{But why do you assume I wouldn't know? Well, of course I didn't, but umm…}

Anyway, this was how she entered the Murong Family's estate.