\chapter{Journey to Shenyang (5)}

Certainly, it was convenient having a horse.

First, you don't have to walk on your own two feet.

Second, it can carry quite a bit of luggage.

It's even pretty fast.

Above all, a horse was beast of inntelgence that could drive autonomously!

Moreover, even without any special handling the horse will follow the road on its own, even avoiding dangers with its built-in safety features!

Back in Qing's homeland they said 'There are people who've never ridden a car, but there's no one who's ridden one just once.'

However the ride quality is somehow…

Horses were living animals, and while there might be some general traits based on breed, each has its own personality.

Just like dogs of the same breed can have wildly different temperaments, horses were no different, starting with how they walk and run.

Some horses try their best to provide a smooth comfortable ride, careful not to jostle their rider.

Others get so excited the moment they step outside that they bounce around. It might look lively to onlookers but was anything but pleasant for the rider bouncing up and down.

Wang Gungdung was very lazy and deliberately took it slow.

Even though she whipped the rein and urged it to speed up, he pretended not to notice and just kept going slowly.

\textit{But this bastard Lü Bu?}

\textit{This one's ride quality is especially terrible.}

\textit{The up-and-down shaking isn't just a light bounce, it's more like my pelvis lift off the saddle with every step.}

\textit{When crossing mountains it was just a bit rough, but the moment we entered the plains of Chaoyang County, a hundred li stretch in the Qian Shan Mountains basin, the ride quality turned downright disgusting.}

\textit{But if I don't taps to scold him, he'll subtly pick up speed. Almost like he's protesting because he wants to run free.}

If Lü Bu knew what Qing was thinking, it would've been deeply offended, thinking 'What a sensitive person'.

Unlike the packhorse Wang Gungdung, Lü Bu was a warhorse, the leader of its herd, the beloved steed of a Mongolian warrior, who once galloped freely across the grasslands. Warhorses wanted to run.

Since he was deliberately bouncing around and protesting to his master, it could be said that Cheong read the inner thoughts of this beast quite amazingly.

But Lü Bu's tragedy was that such protests didn't work on Qing.

In fact, horseback riding demanded considerable physical strength.

Especially the lower body including the waist needs to be strong and sturdy!

You had to grip the saddle tightly with your thighs, and the constant up-and-down motion means your pelvis takes a beating, requiring your waist muscles to constantly adjust for balance.

So when an energetic horse protested with a rough ride, it was not easy for the rider to endure.

However, if you let it run full speed for a while to tire it out, it usually calmed down.

But Qing's body wasn't weak enough to be worn down by a warhorse's tantrums.

In fact, Qing's horsemanship was not great, or to be blunt, it was bad.

So rather than saying she was riding the horse, it was more accurate to say she was perched on it or clinging to it.

Riding techniques originally existed to reduce the high physical exertion required of horseback riding.

In other words, if you could handle the physical toll, you don't need to be skilled at riding!

Just as a strong body spare the mind, a strong body also spare the need for technique!

But Murong Jun being young didn't know this truth yet.

So to him, Qing looked incredibly uncomfortable.

Her head was bobbing up and down by half its height even at a brisk trot.

Thanks to that, the movements of the other heads attached to Qing's body were also quite intense.

"Beggar Sister, it seems like Lü Bu wants to run."

"Hmm. I thought so."

"Beggar Sister, should we let it run?"

\textit{Hmm, something about the way he said 'Beggar Sister' felt off.}

\textit{If he'd just said 'Sister should we run?' it would've sounded mischievous, but 'Beggar Sister' made it sound like we are stealing food and running away.}

\textit{Maybe that's why hearing the 'Sister' part doesn't feel weird.}

Qing shook her head while thinking this.

"Spoiling animals ruins them. This brat's trying a cheap trick. Its previous owner must've been a real sweet-talker."

"You shouldn't treat horses like that. Especially warhorses. They get even more temperamental if you don't let them burn off energy."

"Wait, that actually makes sense?"

\textit{Come to think of it dogs, especially large breeds or herding dogs, develop behavioral issues if they don't get enough exercise. Huh, so it's like a dog.}

"Fine, I'll go for a quick run."

"Huh? We're not going together?"

"It'll take all day and you'll get tired."

As the horse's speed increased, the rider's stamina consumption also increased significantly.

The lighter the rider, the more difficult it became, especially if he was light, weak, and even had short legs.

"Uh, Beggar Sister? I'm Murong Jun, remember? A Murong?"

"Huh? So, you're a Murong? What else? A standard? A benchmark? A treaty? An international standard?"

"Is 'International Standard' even a surname?"

"Maybe if you look hard enough? I heard that some barbarians have three- or four-character surnames."

"Hmm, if I had to pick a fake name, Zhang Jun would be better. Zhang surname is quite common, isn't it"

"Kim Lee Park—no in Zhongyuan it's Wang Li Zhang. So the most common-like is Wang Jun?"

"Wang Jun, sounds a bit off don't you think?"

"Really? Doesn't it sounds like a waiter's name?"

To an outsider this conversation would've been baffling.

What kind of tangent was this?

For the record, there was one more person present, the silent Warrior Lu.

But he was already under Qing's spell, so je was just smiling contentedly at this nonsense exchange.

\textit{How kind and accommodating the Heavenly Blossom Sword is to the child. A woman who loves children is proof of good character, she'd make a great mother.}

"Anyway I'm Murong Jun. Of the Murong Family."

"Wow, that's so amazing, I had no idea."

"Ugh, that's not what I meant."

"Then what?"

"Do you really not know?"

"I knew you were a Murong before we became secret friends."

"Our family is famous for horsemanship."

"Huh? Really?"

But Qing didn't know.

She usually didn't know much, but this time she had a right to feel wronged.

While the Murong Family's horsemanship was universally acknowledged as the best in Zhongyuan, no one talked about it openly.

Because praising the Murong Family's horsemanship inevitably led to discussions about their origins.

The Murong Family was originally a Jurchen noble family, one of the Jurchen tribes that once ruled Liaoning.

And the two most infamous horse-riding barbarians were the Mongols and the Jurchens.

So praising the Murong Clan's horsemanship was tantamount to saying 'Your ancestors were rootless barbarian bandits'.

In fact, if not for the Murong Clan's status as one of the Five Great Families of Zhongyuan, they would've been treated as outcasts.

Even now scholars and high-ranking officials in Beijing saw the Murongs as nothing more than barbarians.

"So you're confident in your riding skills?"

Qing glanced at Warrior Lu.

\textit{Just because the Murong Clan is known for horsemanship didn't mean Murong Jun is any good.}

\textit{After all even the world's cutest Zhuge Xiang isn't exactly a typical Zhuge and the hyper-athletic Zhuge Lixian isn't either.}

\textit{Hmm, I miss Xiang. I should've visited her before coming here. I might be going through withdrawal from lack of Xiang exposure. I'll stop by on the way back.}

But Warrior Lu's response was clear.

A nod.

The silent manly guard vouched for Murong Jun with actions, not words.

"Well then, shall we go for a run. Lü Bu—!"

Neigh! Lü Bu, recognizing its name, instantly cut Qing off with a loud whinny.

Then without even kicking the waist or pulling the reins, it took off at full speed.

And so the gallop began!

And the gallop ended.

Lü Bu was indeed a legendary steed.

Murong Jun's and Warrior Lu's horses were completely exhausted, panting heavily, and sweating profusely (horses sweat a lot, it literally pours out). The cold weather made the horses steams like dumpling steamers.

Lü Bu finally become more docile, having burned off his energy. He was sweating lightly and showing no signs of fatigue.

"Still, it's surprising. I thought it'd just charge off on its own, but it's suddenly so well-behaved."

"Ah. that's because it's a leader horse. Leader horses were like that, they enjoy leading the herd. They're said to be power-hungry."

"Hmm,  horses craving power? Well, I did notice that when it ditched its dead owner for me."

Anyway.

\textit{A hundred and eighty li east of Jianping.}

\textit{Much faster than I expected, thought we'd arrive by sunset, but it only took half a day.}

\textit{Or is it a quarter-day? Wait, is a half-day half of a full day or half of daylight? Am I mistaken?}

The correct answer was 'both'. The term half-day can mean either half of a full day or half of daylight.

Regardless, they arrived in Chaoyang County.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Upon reaching the inn, the first order of business was of course food. This was a normal routine for Qing.

This rule applied no matter what time they arrived at the inn.

Even though they arrived at an awkward time, somewhere between lunch and dinner, Qing ate anyway.

Afterward, she soaked in hot water boiled during the meal, scrubbing off the grime accumulated from her beggar life, it felt like heaven.

Do you know the bliss of washing hair left unwashed for over ten days?

\textit{Wow, this is the best. No words can describe it, I'm dying of happiness.}

After a thorough sweat session—

Especially since Qing was in a state of near-immunity to cold and partial immunity to heat, she couldn't sweat unless soaked in scalding water, making this all the more ecstatic.

And finally freed from the scratchy rags she'd been wearing. Well, who wants to put on nice clothes before bathing?

\textit{It's been a while since I wore silk clothes, and the sensation of Awakening Sense of my skin gently brushing against the silk causes a strange pleasure to rise.}

\textit{Ah, this is why I play beggar sometimes.}

Now refreshed, Qing, who had cast off the persona of Grand Supreme Beggar and assumed the identity of Heavenly Blossom Sword, returned to the reserved table by the railing.

\textit{I had already eaten dinner, so now it is time for dessert.}

\textit{Rice is rice, and dessert is dessert.}

A woman's bath was long and Qing's was no exception.

Murong Jun, who'd come down earlier, looked oddly disappointed when he saw her.

\textit{What? Why the disappointment?}

Qing tilted her head.

"Huh? Why? Oh, does Jun'er still not know what I look like? Because of the veil? Did you want to see my face?"

\textit{Now that I thought about it, that might be the case.}

\textit{First time we met, I was a beggar, the second veiled, then a beggar again with the human-skin mask flipped inside out, and now unmasked but still wearing a veil.}

\textit{I didn't hide it on purpose, but the timing never lined up.}

But Murong Jun shook his head.

"No, not that. It's just… Hup!"

He quickly covered his mouth.

Qing's eyes sparkled mischievously.

\textit{Just what? Did he believe the rumors about the ugly flower beggar woman? Had he not heard the tales of the Heavenly Sword's beauty? Or did he not believe them?}

"Ah sorry! That iss a bad thing to say, isn't it?"

"Hmm. But at least you know it is bad. I'm so proud I could cry."

"It's just… Beggar Sister don't act like a beggar anymore. I liked it when Beggar Sister looked more beggar-like."

\textit{What? Is he teasing me? Right after saying I'm proud of him?}

\textit{Watch your phrasing, kid.}

Qing nodded sagely.

"Hmm, so our Secret Friend likes beggar-like things? Well, to each their own. Quite the unique taste."

"But you're a chivalrous hero…"

"What kind of logic connects beggars and chivalrous heroes? You're only a hero if you act like one."

"But… it's cool when you like beggar…"

"Hmm, beggar… hmm whatever."

Qing could've unleashed a reservoir's worth of insults to beggars.

\textit{I see, since he's not from old Sects, it seems he has soft spot for Beggar's Union.}

\textit{But why the Beggar Union? Aren't they a bit ambiguous whether they're part of Orthodox Wulin or not?}

But Qing held back.

Insulting something someone likes was incredibly rude.

And nothing's more obnoxious than forcing others to dislike what you dislike.

"Anyway, let's have snacks. I wonder how many they have here. Or should we ask if there's a decent teahouse around?"

At this Murong Jun and Warrior Lu's pupils trembled.

But the guard was a man of few words, so there was only one person voiced it out,

"You're eating again? Even after eating all that dinner?"