\chapter{Journey to Shenyang (2)}

"Actually, you don't have much time. Some of those barbarians escaped, so they could call for reinforcements and attack at any moment. It could be tonight, tomorrow. Maybe even a month from now. If you're lucky, they might be too scared to ever return. But are you willing to bet your lives on that? A wise man would pack up and leave right now."

Jang Dae-in looked utterly bewildered.

Even if they left, where would they go after abandoning the lives they'd built here?

It wasn't just one or two people, over a thousand from Jianping would have to relocate. No city could easily accommodate such a sudden influx.

Of course spring was coming soon. If they could hold out for a month with what they had, they might find work elsewhere.

If they could rent other people's fields, they could somehow make a living.

Although they still would end up living with nothing but grass in their mouth.

"Or you could appeal to the authorities for military assistance and request a garrison. Even if they ignore a few individuals, they can't ignore a whole town. You'd have to build fortifications and the military might confiscate your land for farming. But it's still better than being slaughtered by those barbarians."

"That's…"

Jang Dae-in hesitated.

If a garrison was stationed here, the town's power structure would inevitably shift.

Not to mention the taxes they'd have to pay the state would be higher than the tributes they'd been giving the Mongols. And with the military taking their land, the town's resources would dwindle.

"If that's too difficult, then you'll have to find a way to defend yourselves against the barbarians. Seek protection from a powerful sect or hire a master strong enough to repel them. Since they'd be risking their lives, they'd better be  renowned heroes."

Easier said than done. It was practically impossible.

Even if Jianping had lucrative resources, how many sects would be willing to fight the Mongols to the death? And how many could even afford to?

Masters were even harder to come by.

A master could find patronage anywhere. Why would they risk their lives in this backwater fighting barbarians when they could live comfortably elsewhere?

Zhang Dae-in glanced at Qing then spoke in a servile tone.

"Umm, Grand Supreme Beggar—"

"Enough."

Qing looked at him with indifferent eyes.

"I told you I'm not a hero."

"Please, Grand Supreme Beggar, where are we supposed to go if we abandon our homes? We'll end up on the streets. Have mercy on us, weak and pitiful—"

"You're the same people who showed no kindness when I was weak and desperate. Hmm, saying this makes me sound petty, but I don't think a beggar who just waited for someone to help him did anything right. Still, it's not like refusing to help a beggar is a capital offense right?"

Zhang Dae-in's expression brightened slightly.

Qing frowned.

"That's why I helped you. Being cold-hearted isn't a crime. And more importantly, just because you were heartless doesn't mean I wanted to become the same."

An eye for an eye a tooth for a tooth. Pettiness for pettiness.

But choosing not to help the people of Jianping now wasn't revenge for the past.

The contempt and indifference they'd shown her were just trivial annoyances she'd brushed off.

\textit{Just because no one reached out to me when I was struggling doesn't mean I would turn away or mock others in need.}

\textit{That's why I helped.}

\textit{I drove off the barbarian raiders. Isn't that enough?}

\textit{Now what? Am I supposed to stay here and fend off every barbarian attack?}

\textit{It's not like I saved them from drowning only for them to demand me carry their luggage too.}

\textit{I already defeated the raiders and even told them how to survive. }

\textit{And now they're asking 'What about our homes and property'?}

\textit{What a joke.}

"And even if I were a hero, would it be any different? Heroes are the kind who repay even the smallest kindness with their lives. But since not a single one of you thousand-odd people ever lifted a finger for me, thankfully I don't have to risk my life for you."

Qing hopped onto Lü Bu's back.

She grinned.

"It is disgusting being around you, so let's never meet again. Hah, I finally got to say it. Alright, Secret Friend, should we go now?"

"Ah, ah!"

"What why are you spacing out? I just wrapped things up nicely, if Secret Friend stay it'll look weird."

"Yes."

Murong Jun smoothly mounted a riderless horse.

He seemed accustomed to riding settling in naturally.

Murong Jun fell deep into thought.

Of course now that he was on horseback, he could think about whatever he wanted.

Why?

Amazingly, horses were fully self-driving vehicles! They can run on their own and avoid danger autonomously!

Even in Qing's futuristic homeland, such advanced autonomous travel was impossible due to technological and regulatory limitations. Yet here in this primitive era it was already a reality!

Truly astonishing.

Anyway.

Murong Jun stole a glance at Qing's expression.

\textit{Beggar Sister said she was glad she didn't have to risk her life for those awful people.}

\textit{But she already had.}

\textit{It's common knowledge how fierce and brutal the Mongols' martial arts are.}

\textit{After all, the Mongols had once conquered Zhongyuan and absorbed its martial techniques into their own.}

\textit{Yet when the barbarians revealed their true nature, Beggar Sister had stepped forward without hesitation to stop them. Wasn't that proof she'd acted purely to save lives regardless of the odds?}

\textit{Even though the people of Jianping had been so awful to her.}

\textit{Beggar Sister said she is no xia, but in my eyes, she already is.}

The idol in Murong Jun's heart.

The stern. dignified image of the great hero Murong Chengyi grew fainter, while the carefree unassuming figure of Qing became clearer.

Of course, Qing had no idea the Mongols used martial arts.

She'd probably been just as shocked when she saw it this time.

But even if she'd known, she wouldn't have let the people of Jianping die.

So Murong Jun's overestimation of Qing's knowledge was just a minor error.

Still something nagged at him.

"Umm, Beggar Sister."

"Yeah? What?"

"Those villagers… Is it really okay to leave them like that? They can't defend themselves…"

"Hmm. How should I put this?"

Qing took a moment to choose her words.

If they couldn't protect themselves, then sooner or later they'd lose everything, whether the Mongols came or not.

Or perhaps their own negligence failing to prepare for anything had brought this disaster upon them.

Did they really think they could live peacefully, forever laughing off the Mongols' raids as if they'd last for eternity?

They'd foolishly believed in an unfounded peace and made no preparations, nearly leading to their slaughter.

They didn't pay taxes, so the state had no obligation to protect them.

But was taxation the only option?

If they'd at least showed some 'sincerity' the local officials with informal unofficial tax, the villagers wouldn't be so helpless now.

Or if they'd allied with a decent martial sect.

The only 'master' they'd hired was a Second-Rate fighter who barely knew how to breathe, let alone fight.

Maybe they were afraid of inviting martial sects in fearing the town would be swallowed whole.

Or if the villagers had at least prepared some defenses.

Even if it wasn't full-scale fortifications, what if the city's streets were narrow and chaotically laid out, with prefabricated palisades and barriers that could be quickly erected, with traps and such?.

Then when the barbarians turned on them, they wouldn't have been completely defenseless. They could've bought time to evacuate their loved ones.

But they'd done nothing.

And because they'd done nothing…

Were those with power obligated to help them?

\textit{But isn't that would be too cruel to say to our former Sex Fiend seedling, now my Secret Friend?}

\textit{Jun'er is still a kid, and some truths are too harsh for children.}

So Qing used her ultimate technique.

The secret art of conversation!

Answering a question with a question!

"Well, what do Jun'er think?"

"Um… I don't know… What should we do…?"

Murong Jun was lost in thought.

\textit{At least he is a thoughtful kid. Instead of throwing a tantrum, he wrestled with the problem trying to find an answer.}

There was no word for a while.

"By the way, Beggar Sister, where are we going? Isn't this to the north?"

"Oh. I thought we'd check out the barbarian village, their camp or whatever. I'm worried about the ones who got away."

"Ah."

"If we let them go only for them to come back in a day, that'd be annoying. And if they're preparing for something we can talk them down. Or you know how they live in tents? If they're ready to flee, we might just let them go quietly."

"Ooh!"

\textit{So Beggar Sister had a plan after all!}

\textit{She wasn't just abandoning the people of Jianping!}

Murong Jun's eyes sparkled fiercely.

In Zhongyuan, what was the first passage aspiring heroes memorized?

It was from Sima Qian's Records of the Grand Historian, the Biographies of Youxia:

\begin{quote}
	今游俠，其行雖不軌於正義，然其言必信，其行必果，已諾必誠
	
	Today's knight-errant, though their actions may deviate from justice, are always true to their word, resolute in their deeds, and faithful to their promises.
\end{quote}

Here 'justice' referred to law, and the 'promise' of a knight-errant referred to their oath never to tolerate injustice.

The people of Jianping hadn't paid taxes and had colluded with the barbarians. By law they were heinous criminals.

But they were also powerless, living in lands the state had neglected, just trying to survive by paying tribute.

So, shouldn't a true knight-errant stop the barbarians who'd greedily taken their tribute and then tried to slaughter them?

\begin{quote}
	不愛其軀，赴士之阸困

    They disregarded their own lives and went to the aid of those in distress.
\end{quote}

\textit{That's what Beggar Sister had done.}

\begin{quote}
	既已存亡死生矣，而不矜其能，羞伐其德

    Having already faced life and death, they should not boast of their abilities, and ashamed to flaunt their virtues.
\end{quote}

Don't show off.

Bragging would only be a means to elevate their reputation as martial artists.

But if one truly walked the path of a chivalrous man, there was no need to flaunt it.

Thus in the Western Regions it was said 'Do not let your left hand know what your right hand was doing.'\footnote{Matthew 6:3}

And in a distant island nation of the future they'd say '…It was nothing…!!'\footnote{Oh good god, a One Piece reference! Zoro in chapter 485}

\textit{And now Beggar Sister is quietly heading to the barbarian camp without fanfare.}

\textit{Surely, those ungrateful Jianping people would curse her for leaving them behind. even though she'd saved their lives.}

\textit{But what does it matter?}

\textit{If no one is meant to know, then their gossip is irrelevant.}

At that moment, the idol in Murong Jun's heart shifted again.

The stern heroic image of Murong Chengyi faded rapidly. His transparent figure belatedly reaching out in shock, mouth gaping as if to say something—

But it vanished entirely.

Instead, there was a radiant full-body statue of a hero: Beggar Sister swinging a duck leg like a gleaming sword.

Beneath it an inscription began to form in golden letters, dust scattering as the words took shape.

\textit{This is a \textit{youxia}!}

What a tragic turn of events.