\chapter{Journey to Shenyang (4)}

The southern foothills of Jianping.

A solitary ownerless stone mound stood lonely.

Behind, it a weathered wooden plank bore illegible characters eroded by time.

Whoever lay beneath that shallow grave, what story had they carried denied even a proper burial?

Though their tale remained unknown,one thing was certain: the grave now faced dire peril.

A certain reckless woman was vigorously digging it up.

"Uh Beggar Sister? Why are you—"

"Huh? What?"

Qing pulled a well-dried bundle from the mound and deftly slung it over her shoulder.

"Oh, you buried this here?"

"Yeah. A beggar carrying a proper bundle would look suspicious. But if I just buried it anywhere, I'd never find it again. Yup, this is is it. This familiar weight. Heh, welcome back my beloved."

The sword might have protested.

'What kind of warrior in the world buries their beloved blade in a grave?'

'Grave-robbing had been a common pastime in Zhongyuan since ancient times, what if someone stole it?'

'And before that, the dampness from the cold earth and frost, what kind of swordsman treated their weapon like this?'

But a sword was just a sword. Even if it had complaints it had no way to voice them.

Qing pulled her beloved sword from the grave.

Too long and broad to be a standard longsword, yet not quite a greatsword.

This was the Moonlight Sword! Probably \#10!

'Probably \#10' because whenever Qing returned to Divine Maiden Sect,she left it with Old Man Ban of the Xue Merchant Guild, who melted it down and reforged it each time.

Each time, the precious metals that the Trading Company's employees obtained were mixed in, so while the shape remained the same, the composition differed from the original tenth iteration.

"Oh, so Beggar Sister put up this plank too? To make it look like a grave?"

"Not exactly. But I did put it there."

"Wow. Are these characters? From which country?"

"Who knows."

Qing turned to examine the plank.

The crooked scratches on the rotting wood barely holding its shape.

If she had to compare they resembled the script of the 'Land of Morning Calm' Joseon\footnote{Joseon literally means 'Morning Calm'} beyond Mount Changbai.

But only vaguely. It was a script that didn't exist in this era—one only Qing could read.\footnote{Hangul was invented in mid-15th century, but only spread in late-16th century, and even then some letters were obsolete or added}

\begin{quote}
	Here lies the Moonlight Sword.
\end{quote}

The characters carved with a stone were messy and uneven. The final character 'lies' was barely the size of a fingernail.

For some reason her handwriting in her native script never turned out neat.

And below it an even smaller line.

\begin{quote}
	See you later, bastard.
\end{quote}

Qing let out a quiet chuckle.

\textit{Back when I carved this, I vowed to become a true master and crush them all, so I was venting out my anger.}

\textit{Wow, how long ago was that?}

\textit{Is the hilt of the first Moonlight Sword still buried here, or had the cheap wood rotted away by now?}

\textit{But what did it matter?}

A tearing sound followed.

Qing peeled off the human-skin mask she wore and draped it over the plank. The grotesque pockmarked face sagged like a hideous relic.

Then with a smooth motion, she plucked the tombstone of the first Moonlight Sword and hurled it far into the distance.

\textit{The Plague Ghost had left this heartless city behind, now living well among good people, eating and laughing. There was no need for her in this world anymore.}

\textit{The Moonlight Sword had always been with me, no grave or tombstone is necessary.}

Qing stared at the empty space where the plank had been, then scuffed it away with her, foot smoothing the ground.

Then she gathered her tangled matted hair into a single bundle and tied it back, then pulled out a veil and put it on.

Finally she turned her, voice light and unburdened.

"Former Plague Ghost, now Grand Supreme Beggar, is laid to rest here. Hehehe. Okay, let's go."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Liaoning Province, Tai'an County.

A man clutching a broken sword knelt before his adversary.

Rumors in Wulin spoke of a demon known as the Plunder Demon. \footnote{強奪魔}

His exact realm was unknown but he was at least a master of the Flower Realm. A freak who after a duel would take either his opponent's life or their martial arts.

But rumors were just rumors.

If Plunder Demon truly took lives or martial arts, such tales would never spread.

Those who gave their lives couldn't speak.

And those who surrendered their martial arts to survive?

That was a shame worse than death, no one would boast of it.

Yet rumors didn't emerge from nothing. The man now realized the truth behind the Plunder Demon's legend.

"Your life or your martial arts?"

"…My martial arts."

"Your swordplay then? It didn't seem very profound."

"Guh—! My realm was low so I've only mastered three stances. But my master said mastering six would make me renowned, and eight would leave me unmatched in the world. Such is this sword art."

Plunder Demon snorted.

"Of course the creator would say that. If you were to create a martial art, would you admit it's mediocre, and even if you become a great expert, wouldn't it remain mediocre?"

"Guh…!"

The man bit his lip in frustration.

Plunder Demon cleared his throat.

"Ahem, my apologies. I didn't mean to insult you, just stating facts. What martial art didn't claims to be divine? Fine, show me properly."

"…The first stance of the Eight Trigrams Sword: Yang Hong."

The man demonstrated.

Had Qing been present, she'd have stared blankly into space and suddenly muttered 'Eh, just blue'.

But she was the only one in the world who categorized martial arts by color. And even a blue-border art wasn't to be underestimated.

"Hoh. Based on the Bagua\footnote{八卦; Eight Trigrams}? It is quite sophisticated. What's the Sutra\footnote{口訣; Koujue}?"

"Ahem, I'll recite it for you. Observing the world, the Big Dipper in the North. The Sun and Moon rising in the East, setting in the West the Southern Sky alightm, thus dividing into Eight Trigrams…"

Here was a basic Wulin common sense!

Reciting the Sutra three times was standard, the most talented could memorize it in three repetitions.

And Plunder Demon, who had been listening to the recitation silently, noded his head as soon as the third recitation was finished.

The man paused.

"…You've memorized it already?"

"It's not that difficult of a task."

The man's face twisted.

He'd spent three months painstakingly memorizing those lines.

But it didn't last.

"Ahem. May I go now?"

Plunder Demon shook his head.

"No. You'll die."

"Why? You broke our agreement."

"Agreement? Trust is crucial in agreements. Don't you agree?"

"Of course. So now it's your turn to honor it—"

"Precisely. Especially in martial transmission. Especially when it comes to passing down martial arts. If the Sutra are wrong, your Qi and blood might flow backwards, your upper dantian might be possessed by demonic energy, and you might even become a cripple your True Qi are scattered."

Plunder Demon's expression darkened.

"Did you think could deceive me with your meager realm? I gave you a chance to live, and you betray me like this?"

"Wait, there's a misunderstanding—!"

"Trust is important. You've already tried to trick me. Even if you recite the correct Sutra now, how can I believe you?"

"Hold on, there is a mistake—!"

"Guys, it's training time."

Black-clad figures rushed in from all sides.

The man desperately drew his sword, clashing loudly against theirs.

Plunder Demon clicked his tongue and turned away.

There is no need to see the results.

First, the man lacked the skill to survive againts his disciples.

Second, any disciple who'd lose or get hurt to such a man would die anyway, so there was no reason to look after them.

As Plunder Demon turned to leave—

In the middle of the alley, a woman with an extremely cold expression appeared.

She was chewing neibing (內氷), a primitive ancient frozen confection made by freezing milk with honey on a stick.

"Sword Demon. Haaa a big problem has arisen. Haa haa."

"Yeah, it really looks like a big problem. Stuck to your lips?"

Indeed.

The frozen milk had glued itself to her lips.

Unfazed she replied flatly.

"Correct. Haaa but this problem. Haa I'm melting it diligently. Haaa."

"That's why you should have been careful. Who even eat ice in the middle of winter?"

"Haaah, it's not winter, it's the beginning of spring, but, haa. The big problem isn't the connection between my inner lips and my inner cheek. Haa, ah, finally. It fell off."

"Wait, tell me the problem before licking. That's definitely going to stick again."

"The Mongols failed to capture Jianping. Princess Yuansui's procession won't pass through there."

The Sword Demon's brow furrowed.

"What, those barbarians couldn't even take one village? A backwater without even a single sect?"

"The plan of both ambush in Jianping and your personal hobby, stealing martial arts from imperial guards, are ruined. But the mission stands. Yuansui must die."

"So where's the princess going now?"

"We don't know for sure. But my cold logical analysis confirms she'll pass through Liaoning. Scout carefully."

"That's your advice? If not Liaoning, where else would she go? Would she take a boat and sail to Joseon and loop back? Might as well go all the way to Eluosi\footnote{俄羅斯; Russia} before returning."

"That's plausible. A brilliant unexpected move. Then I'll assist further. My astounding analysis suggests her escort size may grow, or maybe reduced to make it secret procession. However, they could also anticipate my analysis and maintain it as is.."

Enemies might increase, decrease, or stay the same.

Truly helpful advice.

Sword Demon sighed deeply.

"I should've never trusted those barbarians."

Meanwhile the woman kept licking the popsicle, until her tongue stuck fast.

"Ah. Thith ith ugh. Haa haaa."

"You could have just bite it off and eat it…"

Sword Demon sighed again.

But he approached the woman and flicked the frozen milk with his finger.

A piece broke off, separating the stick from the chunk glued to her tongue.

"Oh. Thank you."

Chewing the ice expressionlessly, she bowed slightly.

Yet for some reason, she seemed oddly pleased.
