\chapter{Our Wish is Slaughter (1)}

Where and how did the Tai Ping sell so many people?

In fact, human trafficking was never an easy task for a mere quack.

What good is it to gather a bunch of slaves? Where and how are you going to sell them?

Not only was it difficult to find a place that needed slaves by asking around, but it was also impossible to just show up and say something like, 'Are you having trouble with labor shortages? I have a fresh slave here. Would you be interested?' and start a bargain.

Even if you worked hard like that, if you took care of a person, everything you do, from feeding them to clothing them to housing them and breathing, costed money. How could a mere quack handle such a process?

So there will be a set delivery location.

They are the ones who have the prescription for the cure for the plague, and the ones who came up with this evil plan, so even if you kill them, it is actually beneficial to the pest control world, and they are the home of these beasts!

As Qing's expectations rise to the max!

"Uh, that's not something that's sent anywhere separately, there's a certain person who handles all the transactions in the broker store."

"Ma'am, we never go to the same room."

牙商 (Yashang). Broker store.

The lowest of the five lowest occupations in Zhongyuan.

That's right, they are the ones who buy and sell people.

In Qing's hometown, they're called called human traffickers.

In other words, they only handled distribution, not direct delivery.

It was disappointing news for the body-sick Qing, who had finally had a chance to kill.

No, what if it's black?

Aren't there a lot of crazy people?

Anyway, isn't this a chance for human traffickers to clean up all the garbage they've gathered all at once?

Qing has a history of causing trouble in Heuksi.

To be exact, he caused a ruckus and ran away.

However, at that time, the level of Qing was rather low.

And my friends were even more humble, so they were beyond my reach, unable to stand shoulder to shoulder with me and fight alongside me, and were beyond my trust.

Well, yeah, that's right.

The reason I ran away back then was because I couldn't trust these friends, because they were too weak and I was afraid of getting hurt, so I had no choice but to run away.

But now?

Who am I? Transcendent Flower Mirror, Super Flower Mirror, Cheonhwa Sword.

And my friends are now at least somewhat skilled (or at least a little skilled), so I am at least qualified to be given the honorable position of entrusting my body to them.

With this power, I could probably slaughter all the dirty, idealistic bastards… …

For the first time in a while, a fierce look flashed in Qing's eyes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The date of the opening of the black market was originally four days after the Tai Ping was scheduled to stay.

Now that I look at it, it seems that the opportunity to personally check whether the medicine was effective or not, and the quality assurance period that was supposed to last until the patient got better, had to be inevitably delayed until the day the black market opened.

Since I had to take him in advance and feed him and let him sleep until his eyes opened, it was a very frugal trick to guarantee that the medicine was real while also showing off without spending my own money.

Langzhongdaein first selected patients to be treated with the drug, taking into account age, gender, and the details of the disease.

To find out if the medicine really works, if it does, if there are any side effects, and how it works depending on the patient.

And in the meantime, Qing sharpened her sword in anticipation of the slaughter.

That's not a metaphor, she really sharpened her knife.

"Hmm."

"What is it?"

"I'm wondering why the sight of a swordsman sharpening her sword looks so awkward. Do you even know how to sharpen a sword?"

It was Peng Daesan's great insight.

Well, that's because Qing uses weapons so sparingly.

Even the Moonlight Sword is a disaster if it gets the wrong owner.

When your hands are bored on the road, you can use it as a walking stick. When you see a wild fruit, you can pick it and eat it. When you find something like a kudzu tree, you can use it to dig the ground. When you make a fire, you can use it as a kindling. When you hunt, you can use it to clean the meat. You can also use it to grill and eat meat...

The Moonlight Sword (No. 10) I am currently using is a famous sword that was created by a steelsmith with a grateful heart and by melting down a huge amount of materials.

And as the level of Qing increased, the swords and weapons gained strength from their owner's energy, so he managed to hold on somehow.

But is the Moonlight Sword really the tenth?

This is because each time it is entrusted, it is heated until red-hot, mixed with precious iron collected from the Seolga Sanghoe, impurities are removed, and then hammered again.

If, like Mr. Te Mo's ship in the past, the original materials were no longer left due to continuous repairs, can the ship really be said to have continuity as the same ship?

The closest answer to this is this:

As the owner wishes.

If Qing said it's Number 10, then it's Number 10.

So excited.

How long are the four days I've been waiting for?

Maybe, you can find out from the black market.

What if the dark, evil criminals who came from the Black List, or the Killing List in Zhongyuan, came rushing at me? Wow, just imagining it makes my heart race.

So, finally, Qing leaves the quarantine area, leading the way with the peace sign tied neatly to a rope.

If you could leave at will, it wouldn't be a quarantine zone.

It was already a request, like a plea from a branch manager, and although his identity could not be revealed, he was treated as a noble person who absolutely could not be out of sight, so he was given a military salute and allowed to pass through like an automatic door.

Beyond the south gate of Kunming along the lake.

As I left the city gate at dusk, just as I had seen when I first entered the city, there was a long line of people, each laying out mats, lighting fires, and preparing a meal.

As I went against the line of people lined up along the road, the road soon began to climb uphill and became a continuous mountain path.

After climbing over a mountain like that, a large night city with many red lights hanging from it appears behind the hill at the foot of the wireless tower.

On the back, wrapped in red cloth, the character for shadow was engraved in thick letters.

I knew right away what it meant.

[Welcome to the Shadow City.]

It was a phrase written openly on a tent hung at the entrance.

"What, you say it's black?"

"Well, Heuksi was ruined, wasn't it? That's why a new market was created by a gathering of black market merchants. They changed the name to Heuksi because it would be inauspicious to use a ruined name, but it's just Heuksi, right? Youngsi is a bit of a dirty name, so everyone just calls it Heuksi."

"Hmm. Something. Something."

Qing frowns slightly.

Why, why do I have a slightly ominous feeling? Why, why? What is it? Why?

Something, the atmosphere is really lively?

Isn't it just a night market?

The Heuksi I visited before had a strangely tense silence, as if there was a distrust between the customers and the merchants.

But what about Youngsi?

"Come on, come on, come on! Come on, come on! Come on, come on, come on, come on!"

"Selling fresh produce that arrived today! Ladies, come take a look. I also happened to have quite a few precious-looking trinkets."

"Go see the poisonous plants of the Yunnan Chonglin (tropical rain forest) mountains: the pitcher plant, the oyster mushroom, the poisonous plant, the poisonous plant, the poisonous plant!"

At that, Tang Lan-Ah's ears perked up, and he immediately grabbed Qing's elbow.

"Oh, Qing'er, let's go check out some poisonous plants. The poisonous plants in Yunnan's Chongrim are famous for being very toxic."

"Hey, Lan-Ah, we didn't come here to play, did we? Should we take a quick look and go?"

Qing changes his words midway.

Come to think of it, it seems like we came to play.

To me, killing is a game, so wouldn't it be fair to give them some time to enjoy themselves too?

Qing is dragged away pretending not to win.

The boy standing in front of the poison merchant proudly stretched out his finger and made a gesture.

"Hey, where did you get this? When was it dug up? It looks pretty good, doesn't it?"

"Haha, you're spot on. This is Daerisan, this is Aeroesan, and this is Munsan."

"What, you're saying it's a poisonous weed in the forest?"

"There's a small grove of mosquitoes near the water there, and they're definitely more toxic than you'd expect. Wow, how can I explain this? I can't even tell you to try it."

"Hmm, it's definitely real. Um, Cheo, no, Summer, look here. What do you like?"

Even if you ask me what looks good.

To Qing, it just looks like dried grass.

"Oh, my, they're completely different. Look here. This one has stiff thorns on its stem, this one's slightly pointed at the end, and this one grew in a swamp. It's kind of damp."

"No, they're all the same?"

"It's different, isn't it? Look closer. Look at the spacing between the leaf veins here..."

Whether the leaf veins are straight or crooked, if a poisonous plant is poisonous, it is poisonous. Even if you explain it, it actually looks the same everywhere.

"Hey, you're a very knowledgeable guest. Uh. Are you by any chance interested in the poisonous plants of Yurakchongrimsan?"

"What? Really? Those poisonous plants are the Odokmun-"

"Shh. That's why I'm only showing it to those who know how to treat me like a guest."

"Hmm? Are you sure? How can you believe it?"

"If you lie about the goods' origin, you won't be able to do business in Yeongsi. If you get kicked out of Yeongsi, where will a good, honest poison merchant like me do business?"

Can goodness be placed before a poisonous statue?

No, more than that.

If you lie about your goods' origin, you'll be kicked out?

Originally, if you were fooled by a black market, it was the fool's fault, wasn't it a den of those who were very convenient for merchants, like Yongpal or Chapal in the local language, who were scammers?

Meanwhile, the poisonous snake enters the tent and unrolls the rolled-up bundle.

These are the same poisonous plants that were on the table.

Lan-Ah had a very suspicious expression on her face, but after picking at a leaf and eating it, she screamed, "This is real, this is real!" Her eyes sparkled with excitement.

She bought the whole package and placed it on Zhuge Lixian's back as if it were nothing special, and his expression was filled with pride.

Something, um. This.

Why is it so noisy around here? Is it just a night market where you have to cover your face to enter?

"Interesting, Sister. It looks quite organized. Do you see that skewer stand over there?"

"Yeah. I've been watching you since earlier. Hmm. I heard you shouldn't buy anything at Heuksi. Oh, was that what Zhuge told you?"

"Well, I don't know what kind of meat it is. But, you've marked the skewers with the raw meat label? Even the city market doesn't do that. However, I can't guarantee that it's the right raw meat."

Wouldn't it be a skewer of black meat that is labeled as beef, but is sold after being grilled with rats or rotten meat, or in the worst case, could even be human flesh?

I held back my regret.

This hunger will be filled with my blood.

I've got all the human traffickers out. I'm going to cut them into seventeen pieces, all at once, into a very pretty star shape.

So, suppressing his urge to kill, Qing pushed forward, saying that today was the day to hold a funeral for the human traffickers.

"Wow, Xiao-mei, look at this. Isn't it pretty? My niece, look at this? What do you think?"

"Oh, oh."

"Do you like it? Ooooh, is this gold…?"

"Hehe, oh no, it's not gold, it's pyrite. But if you wipe it with a clean cotton cloth every once in a while after going out, it'll be just like gold."

"This. This is me."

"This? Does my niece like this? Excuse me, how much is this?"

"Customer. That's a store keeper's item. Is that okay?"

"The treasure?"

"You mean it came from a grave? A baby grave."

"Ugh, I don't like it… Niece, this won't do."

"Ugh."

Qing tilted her head.

Something, isn't it subtly conscientious?

Of course, a truly conscientious merchant would not deal in stolen goods or burial goods.

Thanks to this, the market atmosphere is not bad.

Although their faces were covered, they had no intention of hiding the sound of each other's chatter, and the customers' footsteps were somehow full of life.

Hmm. It feels like there's a knife fight going on...

After a while of glancing around like that, I finally reached the tent of Asang, the distributor with whom Tai Ping had contracted to supply.

In front of the tent, a man stands with his arms crossed, while a man with a long sword tattooed on his eye sits with his arms crossed, staring blankly.

I've felt this before, but I wonder if human traffickers give extra points to people with dirty impressions during interviews. Why are all physiognomies like this?

Are people with dirty faces trafficking people, or is this why physiognomy is considered a science?

While Qing was thinking for a moment, the man shook his head and spoke.

"A piece of silver."

"hmm?"

"His back is hunched, and he got some flesh on him, but no muscle at all. Where should I sell this idiot? So, a little bit of silver. It'll be the same no matter where you go. No, this is a generous payment."

It seemed that the tied-up Tai Ping was something that Qing had come to sell, as if she was a human trafficker.

"Hey, ahem. I'm going to die……."

"What, who are you to pretend to know, um, Congressman Tae? No way, Congressman Tae, what the hell—"

The man jumps up and the chair falls backwards with a thud.

Okay, that's a good response. Now, let's wait until all the goons are called, do a cool sword dance, and then have them tell us where they've taken the people. That'll be perfect.

It was a moment when the corners of Qing's mouth curled up.

Thud, the man immediately falls to his knees.

"All the goods he brought were handed over to the Gaeguhyeon Jeonggajang! We didn't touch a single hair on them! It's true!"

A loud answer came out without even asking.

\begin{lstlisting}
	The chapter's title is a reference of 1947's South Korean song, '우리의 소원' (Our Wish)
\end{lstlisting}