\chapter{Our Wish is Slaughter (3)}

Qing returned to the quarantine zone of Kunming and relayed the information she had gathered to Lanzhong Daren.

"So, I haven't obtained the prescription yet, but I'm planning to visit a place called the Zheng Family Estate in Gejiu…"

"Hmm, that's strange. But why do you look so down? Did something happen?"

"No…"

Her voice lacked energy, and her shoulders slumped as if all her strength had drained away.

Lanzhong Daren, about to press further, quickly backed off. An old man who's lived long enough knows when to hold his tongue. 

Besides, she's a woman after all.

Of course, it wasn't that. It was more like a severe lack of slaughter—a kind of spiritual malnutrition (of slaughter).

"But what's so strange about it…?"

"Well, I've never heard of this Zheng Family Estate, and what kind of fool would set up a tea plantation there?"

Suddenly, Qing's eyes lit up.

"Something's suspicious! Very suspicious! I smell a conspiracy…!"

"No, it's not suspicious—it's just stupid. Tea grown there would be bitter and astringent, hardly worth selling."

"Huh? Why?"

"I don't know. That's just what I've heard since I was a kid. If you ask why our village doesn't grow tea, they'd say the soil isn't suitable or the leaves are too spicy."

"Your village?"

"Ah, didn't I mention it? I'm from there. A place called Noji Village. It's nearby."

For the first time, Lanzhong Daren revealed a personal secret—his origins. A wanderer among wanderers, he had no hometown to speak of, but he didn't seem to be hiding it either.

"Ah, so it's your hometown. But you've never heard of the Zheng Family Estate?"

"Hometown? What hometown does a wanderer like me have? It's been over twenty years since I last visited. They say the landscape changes in ten years, let alone double that. If what you say is true, it seems some outsider with money has set up shop there. But if they're foolish enough to try growing tea, they won't last long."

"Could they be up to something shady?"

"Would people involved in shady business leave such obvious traces? It's probably just some nouveau riche from outside. That area's known for its clannishness, and the more rural it is, the worse it gets. They're probably just waiting for him to fail."

"Huh, that sounds plausible…"

Qing's eyes lost their spark again.

\textit{This intuition of mine is really off.}

\textit{Surely, if we go to the Zheng Family Estate, the old man's words will prove true.}

\textit{Isn't it just another closed-off, exclusive village in Zhongyuan?}

Villages in Zhongyuan welcome tourists but turn hostile if you try to settle down.

In fact, it's understandable.

Who would leave their hometown and wander to a foreign place unless they had done something wrong?

They must be criminals who committed unforgivable acts, even by the lenient standards of local customary law.

Some villages are even hostile to tourists, building walls to completely reject outsiders.

So, when a wealthy outsider tries to settle, the locals will try every shameless and cunning trick to squeeze money out of them.

But this isn't unique to Zhongyuan—it's a universal human nature.

Rural areas everywhere are nightmares for outsiders.

Even in Qing's homeland, countless people who dreamed of returning to the countryside ended up scarred—economically, physically, and mentally—by the harsh and insular local mentality.

"Ugh, I can't even be a righteous swordsman anymore…"

What is a righteous swordsman?

Someone who rises against the countless villains of the world, wielding their sword for justice.

They cut down villains to avenge the oppressed, crushing their skulls to show that justice still exists in the world, that evil is punished.

\textit{But is this how it's supposed to be?}

\textit{I'm trying so hard, yet it's so difficult to get a taste of action these days. Everywhere I go, villains line up, but it's never satisfying…}

Qing slumped again.

Lanzhong Daren shook his head slowly.

\textit{Come to think of it, she hasn't been normal since the beginning.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Cutting off Tai Ping's wrist was put on hold for now.

Though he's not a physician, he's at least someone who knows how to make medicine.

You need skill to fake it—you can't just scoop up some water and call it medicine or sell black lumps as pills.

Lanzhong Daren decided to keep him around as a servant while researching the cure.

Qing considered leaving Tang Lan-Ah behind, but it didn't seem right to ask her to stay when she wasn't here for tourism.

"Will you be alright, Senior?"

"I promised to save this man's life, so I'll stay by his side until you return. Besides, I've already taken his money."

Tai Ping felt deeply wronged.

Aside from the debt for the cure, he had paid a hefty sum to Tiger-slaying Sword for protection.

But now, having taken the money, Tiger-slaying Sword was essentially holding him hostage to prevent him from escaping.

Tiger-slaying Sword's logic was simple.

If Tai Ping runs, Qing will kill him.

So, if he runs, he dies.

Since he owed Tai Ping his friend's life, he can't be left to die.

Therefore, he must be closely watched.

Tai Ping was beyond wronged—he was on the verge of madness.

But regardless—

"Hehe, take care on your journey, Miss. I've always admired Lanzhong Daren to the heavens, so I'm deeply grateful for this opportunity."

Seeing how close Qing was to Lanzhong Daren, Tai Ping hoped to earn some goodwill by diligently assisting him, thus securing his safety.

Qing pointed to her eyes with two fingers, then turned her wrist to point them at Tai Ping.

She'd be watching, so he'd better not get any ideas.

"Hehe, how could I dare?"

"Good, let's do this right."

"Yes, I'll do my best."

And so, they set off.

Gejiu was about 500 li away.

For the people of Zhongyuan, 500 li isn't that far.

An ordinary civilian could walk 50 li a day, so it would take about ten days—a round trip would be less than a month. For martial artists with their superhuman abilities, it's practically a stone's throw.

But Qing, brimming with energy, glared at innocent villagers with bloodshot eyes, threatening them as they passed through various villages.

"Excuse me, are there any villains around here? Someone who deserves to die, someone who should be punished by heaven?"

"Hmm, not really, Great Expert."

"Don't hold back. I'll handle it cleanly, no repercussions. Are you being watched? Do you need help? Just blink if you do."

"Ah!"

"Oh, so there is something?"

"Lately, the ones causing trouble are those Bai people. That Bai plague is causing chaos. What are they eating to spread such a terrible disease?"

"Hush, don't say that. It's just an unknown illness, don't spread rumors."

"Oh, Great Expert."

The villager looked around and whispered.

"They say it's all a plot by the Bai people. They're trying to rebuild the Dali Kingdom and wipe out other ethnic groups by spreading this disease."

"What? Who's saying that? That the Bai people are deliberately spreading the disease? And rebuild the Dali Kingdom? The Dali royal family is still intact."

The emperor of Dali had voluntarily surrendered to Zhongyuan centuries ago, earning the title of Dali King for his loyalty.

When the Zhu family's founder waged war against the previous dynasty, he promised to preserve the Dali royal family in exchange for their neutrality.

Though downgraded from emperor to king, the Dali royal family still exists.

"It's just an illness. Diseases don't discriminate by ethnicity. Don't spread such rumors. There's already a prescription and medicine, so it'll be over soon. Don't worry too much."

"Oh, is that so? What a relief. We were worried it might spread to our village."

"So, no villains? No bandits or swindlers?"

"Hmm, nothing comes to mind."

"Hmm…"

It seems Yunnan is peaceful, aside from the plague. Sad news for Qing.

Is it the heart of a righteous swordsman to feel sorrow in peace? Regardless.

Out of curiosity, she asked about the Zheng Family Estate.

"The Zheng Family Estate? I'm not sure."

"The Zheng family? Was there a Zheng family in our village? Ah, Gejiu? How would we know about that?"

"Ah, I've heard of it. Some rich young master moved in a few years ago."

"The Zheng Family Estate? Didn't they set up a big orchard? It's only been about three years. Do they think fruit trees grow in three years? It'll take at least ten years to taste the first fruit."

"Ah, the Zheng Family Estate? I heard they made a fortune in Hangzhou. Yunnan has so much land, they're trying all sorts of businesses. How much gold do they have to do all that?"

Fortunately, as they got closer to Gejiu, more detailed information about the Zheng Family Estate emerged.

About five years ago, they built a grand manor and started planting apple, persimmon, and pear trees across the mountainside.

And recently?

"Ah, lately they've been looking for people to mine coal. They found a coal vein while planting fruit trees. But who would want to mine coal?"

Coal, known as "maetan" in Qing's homeland, has been used in Zhongyuan for over a thousand years, shaping their cooking style with its high heat.

Since coal is commonly found when digging into mountains, it's not strictly controlled by the state.

But mining coal is a gamble—the quality and quantity of the coal are unpredictable.

Wealthy people often receive investment requests from prospectors carrying hand-drawn maps.

Finally, they arrived in Gejiu.

After gathering information along the way, the conclusion was clear.

Yunnan is peaceful.

And the Zheng Family Estate is lucky.

While planting a large orchard, they accidentally discovered a coal vein and decided to start mining.

So, why recruit miners in such a sneaky, underhanded way?

"Well, Miss, isn't it because Yunnan is so abundant? It's warm year-round, so you won't freeze even without a house. The land is rich, so you can survive by foraging. That's why Yunnan people are known for being laid-back—lazy, to be blunt. So, even if you offer extra money, it's hard to find miners."

Qing's shoulders slumped.

\textit{Of course.}

\textit{What was I expecting? Some grand conspiracy?}

\textit{No, what was I thinking?}

\textit{Peace is the best, so…}

They say calm follows frustration.

At this point, Qing felt oddly refreshed.

\textit{Chasing the taste of blood, I've come all the way to Yunnan, yet I can't even relax.}

\textit{I should've enjoyed the local cuisine and sights with my friends. What was I thinking?}

\textit{It's all regret, regret.}

A clear light returned to Qing's eyes, characteristic of Taoist enlightenment.

However, Zhuge Lixian's expression remained troubled, his brow furrowed.

"But even if the pieces fit, how does this connect to the cure for the plague? How did they use the prescription as bait to lure people in?"