\chapter{Our Wish is Slaughter (4)}

"I don't know much about pharmacology, but how did you manage to obtain a prescription that even Lanzhong Daren couldn't find? What do you think, Sister Tang?"

"Well, it's not always about the level of medical skill. Sometimes, it's just luck. For example, if someone claims to have recovered from an illness on their own, we can investigate what they consumed."

"As you've seen on the way, this area doesn't seem to be particularly affected by the plague. Whether it's because the Bai people don't live here, I can't say."

The Bai people mainly live around Dali County and its vicinity, while the southeastern part of Yunnan is a region inhabited by various ethnic minorities like the Zhuang, Yi, Hani, Miao, and Yao.

"Hmm, or perhaps it's a local endemic disease? Folk remedies often get passed down alongside such illnesses. If there's data on that, it might be easier to combine the medicinal ingredients."

"But didn't Lanzhong Daren mention he's from this region? If it were a Yunnan endemic disease, he would've known about it first."

Hmm, seeing them discuss like this, they really do seem smart.

After all, Zhuge Lixian is known for his sharp mind, a muscle-bound genius.

Tang Lan-Ah, despite her sharp personality and lack of manners, is an acknowledged physician and poison master from the Tang family.

They don't just *seem* smart—they *are* smart.

Of course, since their cultivation level isn't high, they need to rely on their intellect.

And then there's me, a martial arts prodigy.

The youngest to break records in Zhongyuan, a rising star in Wulin, and a transcendent martial artist who has surpassed the limits of cultivation—Qing, the Heavenly Flower Sword.

Qing glanced around.

Still, she's more than just a pretty face—she's the most beautiful.

Himae might be a blockhead, but he's at the peak of the late-stage transcendent realm, just a step away from the Flower Realm, making him a proper master.

Our Ciyu isn't particularly talented in martial arts, and her intellect isn't great either, but, well, as long as she grows up healthy, it's fine. She's rich, after all.

Qing's gaze landed on Xue Iri.

But our Gunyeong, seeing her like this, well, she's a transcendent, but she only reached it by mastering ice techniques, so she's practically disqualified. She's not smart, and she's not sociable either. What are we going to do with her? It's enough to make me cry…

"No."

"I didn't say anything."

"No."

"Stay strong."

Qing patted Xue Iri's shoulder.

A subtle frown appeared on Xue Iri's brow.

"Alright, enough. Anyway, the conclusion is that it's suspicious, right? If it seems like we won't reach a conclusion, there's no point in overthinking it. Let's just go and ask. If your body is strong, there's no need to strain your brain, right?"

Thinking about it, the most important thing is the cure for the plague.

First, we need to get the prescription for the cure.

If we offer a fair price and they refuse?

Well, it's obvious they won't sell it. They're using it as a stable means to secure mine workers, even if they have money.

If they stubbornly refuse to sell, there's no other choice.

We'll have to threaten them with swords.

The medicine seller has already traveled through several cities, so he's had enough time to profit.

And so, Gejiu, the Zheng Family Estate.

A grand manor stood alone amidst vast fields on the outskirts.

Qing had already cleared her mind.

They say that if you seek fate, it eludes you, and if you force it, it ends badly. If it's truly fate, it will come naturally without effort.

So, won't the slaughter I long for also come naturally?

But then?

"Stop. The manor is currently not receiving guests."

Qing frowned at the bright red numbers floating above the gatekeeper's head.

What's this? Why is his evil karma so high? He's a complete scoundrel! And both of them?

However, evil karma doesn't guarantee the current state.

It's something Qing has learned from observing countless numbers.

Evil and good karma have no statute of limitations—they only increase or decrease based on actions, regardless of one's current mindset.

Even if a former villain repents and becomes virtuous, their evil karma isn't reduced.

In other words, high evil karma doesn't necessarily mean they're currently evil.

That's why even if Qing always sings, "I want to kill, ah, I really want to kill villains,", she first gauged whether they're truly deserving of death before drawing her sword.

Perhaps they committed great sins in the past but have since reformed and become virtuous gatekeepers.

But regardless, her guard was up.

Originally, she planned to politely introduce herself and enter as a guest. After all, few could refuse a visit from the Heavenly Flower Sword and the disciples of the Five Great Families.

But the gatekeepers' evil karma was like this from the start?

"I'm a wandering, nameless swordsman. I'd like to meet the master of the estate."

"……?"

The gatekeepers' mouths hung open.

It was an utterly baffling statement.

A wandering, nameless swordsman?

He was outright refusing to reveal his identity.

On top of that, he wore a mask and carried a large sword at his waist.

Where in the world would a gatekeeper trust and guide a suspicious figure who won't even reveal his identity to their master?

Qing clicked her tongue again.

"First, could you contact the master? I have some inquiries regarding Tai Ping, the medicine seller who supplies slaves to the Zheng Family Estate."

"Ah, yes. Please wait a moment."

One of the gatekeepers said this and quickly ran into the manor.

And after a short while.

"The master has agreed to meet you."

Zhuge Lixian's eyes sparkled as he immediately understood the flow of events.

After all, low-level employees have no choice in such matters.

If this were a military gate in his hometown, it would be like a stranger approaching a guard on duty and saying:

"Who am I? That's none of your business. Contact your battalion commander. I have something to say about Kim, who's been skimming supplies from the battalion."

The guard can't decide on his own to tell the stranger to leave.

He has to relay the message and receive instructions on how to respond.

And from the master's perspective?

Whether it's good or bad news, it's related to him, so it's hard to refuse.

He needs to know whether the mysterious visitor's message is good or bad news.

That's why, despite the obvious suspicion, they could immediately go to meet the master of the Zheng Family Estate.

Zhuge Lixian was deeply impressed.

As expected of Sister, she's occasionally a genius.

Qing, though rarely, sometimes displayed a kind of natural, sharp insight and keen intelligence in her words and actions.

It's just that she doesn't use her brain often. Why waste such a good mind?

Of course, as she often says, "If your body is strong, your brain can relax." Sister is a transcendent martial artist with innate divine strength.

Regardless, Qing's eyes rolled.

Hmm, the other servants don't seem to have particularly high evil karma. Maybe those two were just exceptionally scummy?

In fact, it's common for close friends to pair up for guard duty, and birds of a feather flock together. If those scoundrels got along, it's not entirely impossible.

"Master, I've brought the guests."

-Please enter.

Upon entering the master's office, a young man who looked no older than thirty, unusually young for a master, raised his head.

I heard he's a young master.

And the moment she saw him.

Qing, who already had large eyes, widened them even further. Anyone seeing her might think her eyes would pop out.

At the same time, her heart began to race.

\textit{Wow! Evil karma! Twelve hundred points!}

Four-digit evil karma is not something you see every day.

Of course, in Zhongyuan, the richer and more powerful the merchant, the higher their Evil Karma tends to be.

But this far exceeds the average.

"I'm Zheng Liuzhang, the one managing the Zheng Family Estate, though I'm not much."

\textit{Zheng Liuzhang? How can someone's name be "Train Station"?}

\textit{Then, if he has a brother, would his name be "Bus Stop"? Or "Terminal"?}

"And you are…"

"Enough. Tai Ping, you know him, right?"

Qing coldly cut off Zheng Liuzhang.

Zheng Liuzhang forced a troubled smile.

"You said you're a wandering swordsman, right? First, let me clarify, this is a misunderstanding."

"A misunderstanding? What misunderstanding?"

"It's true that I hired Tai Ping, but it was only a plan to recruit mine workers. It was never any kind of underhanded scheme."

As if he thought they already knew everything, Zheng Liuzhang readily confessed.

And confessing readily means he's prepared his excuses.

"Go on."

"As you know, there are hardly any people willing to work as miners. Even if we offer extra money, they quit after a few days."

"So, you pushed those who sold themselves to pay for medicine into the mines?"

"'Pushed' is a bit harsh. We've been treating them well. We pay them generously, and after the contract period ends, we deduct ten gold coins and pay the rest. We've even notarized it."

His recruitment methods might have been forceful, but he claims to treat them the best.

But with his evil karma being what it is, how can we believe him?

"It's true. You can go to the mines right now and check for yourself. From the workers' quarters to their meals, you can see for yourself and even ask the workers. We've promised to contact their families later, but it's still too early."

"Too early?"

"As you know, we can't keep recruiting workers while the plague is ongoing."

"So, you'll keep luring miners with the cure until the plague subsides? You have the prescription for the plague but are keeping it hidden?"

"We have no choice. The cure isn't ours. However, the other party has promised to release the prescription at the appropriate time, and only then can our workers contact their families."

What? What's this now?

Qing's expression soured.

\textit{So, the cure for the plague wasn't made by the Zheng Family Estate.}

\textit{They got it from somewhere else.}

\textit{What is this, some video game quest?}

\textit{Like, complete one stage, draw a line, and then move on to the next task in another town?}

\textit{Investigate the cure at the Zheng Family Estate (Complete).}

\textit{So, what's next? Dismember Zheng Liuzhang, the master of the Zheng Family Estate, and find out the whereabouts of the cure?}

"Enough. So, where is this 'other party'? Who completed the prescription and is secretly hiding and distributing the cure?"

"I can't tell you due to the contract. Please consider our situation. What's left for a merchant if we lose our credibility?"

"Hey, do you know who I am?"

"Well, I don't know. You haven't told me yet. So, may I ask who you are, honored wandering swordsman? Ah, by the way, how could a mining business be possible with just the strength of one family? We also have several benefactors helping us."

His words were polite, but the underlying meaning was clear.

'Who do you think you are? You seem to have some influence, so go ahead and make a scene. We're not to be trifled with either.'

Zheng Liuzhang smiled smugly.

But it didn't last.

"You don't know who I am, right?"

"So, if you'd just tell me, wouldn't that solve it?"

"No, this is frustrating. Don't you get it? A swordsman of unknown identity is sitting in front of you right now. Here, look at this, shiny shiny. This is Sword Force. Can you do this? Can you block a sword with Sword Fnergy and then use qinggong to escape? No, even if you manage to escape, what then? Are you going to report it to the authorities? Someone suddenly attacked me, their name? I don't know. Their face? They were masked, so I didn't see it, but please find and punish them?"

Only then did Zheng Liuzhang's expression harden.

He finally understood the meaning behind Qing's 'Do you know who I am?'

\textit{Do you know who I am? You don't, right?}

\textit{Then, no matter what I do, there'll be no repercussions, right?}