\chapter{Our Wish is Slaughter (5)}

"What, what kind of outrageous nonsense is this! A merchant's contract is—"

"Well, I'm not a merchant, so I don't know. But it's a good thing for those who have the cure, right? I'm willing to pay a fair price for it."

It was baffling how the person who had just threatened them with repercussions was now talking about paying a fair price.

"And who would think we've run into a gang of bandits? A wandering swordsman wants to do some good in the world, and instead of bowing deeply and cooperating immediately, what's this?"

"What kind of tyranny is this! There's no such law in the world!"

"Of course, there's no such law."

Qing tapped the hilt of her sword.

"But the sword is right here, isn't it?"

Qing was unapologetic.

The law is far, but fists are close.

And this wasn't just fists—it was a sword.

If Zheng Liuzhang had been an ordinary merchant—with ordinary evil karma—Qing might have felt a bit sorry.

Obtaining the cure's prescription was an extremely important matter, and it was for the sake of the world.

To save the sick by uncovering the cure, prevent future patients, and avert countless tangible and intangible damages caused by the plague.

But could such a cause, justice, and public good justify one-sided sacrifice?

To put it precisely, is it permissible to rob the rich to help the poor?

But there were also clear cases.

If the rich had not earned their wealth properly, if they had accumulated ill-gotten gains through the blood and tears of countless people?

Then, of course, you could rob them without hesitation.

You could strip them bare without a shred of guilt.

"With such a grand estate, an orchard, and a mining business, haven't you had enough? Instead of helping with a good cause, you're still raising your price for petty gains? You scoundrel! Unforgivable!"

Qing stood up and shouted.

It was a radical, escalating anger.

Zheng Liuzhang was stunned, his mouth hanging open, but his face turned pale at the cold sound of a sword being drawn.

"Wait—"

"The blade moves at a speed of fifty thousand li per moment toward the arm of the Zheng Family Estate's master."

"What—"

"And when the master's arm is half a foot away from the blade, at that moment, reveal the source of the cure. Five, four, three—"

"Wait—"

"—Two. One."

Qing's hand shot up.

The blade in her hand soared high, and then—

"I'll tell you!"

"Well, you should've said that from the start. You made me draw my sword rudely. It's all your fault, Master Zheng, right?"

"Ugh."

"Now, who provided the cure?"

"B-before that, if you promise to keep what I say a secret…"

"Hmm. Well. Fine. I can do that. If you'd done this from the start, I wouldn't have had to blush. I wouldn't have had to draw my sword and hurt my arm. Isn't it much better to talk like this?"

Zheng Liuzhang was utterly exasperated.

Barging in like this, what kind of tyranny is this? It's beyond outrageous.

Why, what did I do wrong?

Seeing his aggrieved expression, Qing was just baffled.

With all that evil karma, how could he feel wronged?

But wronged is wronged.

People naturally feel wronged only about their own losses. Even if they suffer due to their own mistakes, they feel wronged. How much more so if they think it's not their fault?

As a result, Zheng Liuzhang's voice carried a subtle, damp tone.

"The Five Poison Sect provided the cure."

"The Five Poison Sect?"

"Who else in Yunnan could make the cure for the plague but the Five Poison Sect…"

"The Five Poison Sect, the Five Poison Sect. Why does it sound familiar? Where have I heard it before…?"

Qing muttered to herself.

Five-Poison-Sect. The tip of her tongue touched the roof of her mouth, then jumped to lightly touch her front teeth. Hmm, where did I hear it?

Then Tang Lan-Ah acted like she knew.

"Hey, remember that time in Dogangyeon?"

"Dogangyeon?"

"No, why, that, the greatest chef Bai—"

"Ah! Right. It was those guys."

The one who got hit is mentally scarred and can't sleep easily, but the one who did the hitting forgets immediately and sleeps soundly.

You might think it's the opposite, right?

The perpetrator forgets quickly, but the victim never forgets. The saying about the hitter and the hittee is nonsense, probably made up by someone who's never been hit.

"That, the one who released the Oyang Carp, right?"

Qing had forgotten the Five Poison Sect and Dogangyeon, but she immediately remembered Bai Changja, the world's greatest chef, and the delicious Oyang Carp fish.

Right, those guys were there. It was so fun killing them…

That's about all Qing remembered.

But then?

Ah, this is a bit tangled.

Back then, her methods were a bit harsh. Of course, they were scoundrels who deserved to die, but still, they're not the kind of people you can casually ask, "Can I buy the cure, please?"

Hmm. Well, that's that.

"Now that I've told you everything, could you please leave? I'm quite tired and would like to rest."

"Hey, your hospitality is quite lacking."

"…Guest, you say?"

Qing shamelessly nodded.

"Of course. When a precious guest arrives, the master should personally show them around the estate, explain the business, and let them tour the facilities."

"What are you talking about?"

"Don't you understand? With the plague causing such chaos and the cure's prescription being hidden, I need to check if the people you've taken in are doing well."

It's like entrusting fish to a cat or hot soup to Gunyeong.

How can you trust the words of a scoundrel with four-digit evil karma?

Given the evil karma he's accumulated, it's doubtful whether the families of the patients sent to the mines are even alive, let alone well.

Qing tapped the hilt of her sword again, her voice now devoid of any playfulness.

"Right now."

If he's lying?

Well, the usual scene: whips, shackles, tattered clothes, skeletal slaves, a brave soul shielding a fallen comrade, a cold-blooded overseer, and, hmm, cotton? No, not cotton, whatever.

If that's the case, then it's time for a rewarding exploration of the human body, a deep dive into the mysteries of anatomy, and a profound session of repentance and atonement.

…That's what I thought at the time.

"Oh, no, no. At first, when they told me to mine coal, my heart sank. But where else in the world would you find such luxury?"

A miner, his face blackened with coal dust, grinned broadly.

His crooked teeth made him look even more innocent, but his smile was undeniably satisfied.

They say they're doing well.

In fact, washing every day has even cured their itchiness. The beds are soft, they eat four meals a day, and they even get fish.

Similarly, the women also looked bright.

With so many workers, there's plenty of work to do—cleaning, laundry, cooking, serving meals, and managing the mining village's household.

It was obvious they weren't lying.

What's this? Why are they treating them so well?

"Didn't I tell you?"

"No, why? If you thought we'd make the women do such chores, why did we pay the highest price for a one-year contract?"

"Whether it's men or women, the cost of hiring them for a year is the same. We agreed to pay the men extra wages after the contract ends, so it's not like we're paying more for women."

"No, then why did you specifically target young women and make them work for a year? It's very suspicious and dangerous."

"That's how we get men to come. If the conditions weren't suspicious, we'd have only older women crowding around, not miners."

If someone in the family had to be sold, in this primitive, uncivilized Zhongyuan, the first to go would be the older women.

Next would be the young women, but the conditions sounded too shady, like they'd be harassed or worse.

No one would send their daughter or sister to such a place, so the men stepped up.

"Hmm."

"Are you satisfied now?"

"Ah, why is it true?"

It was the surprisingly honest welfare system of a scoundrel with twelve hundred points of evil karma.

Strange, how could this be?

Of course, I'm not sorry.

If you didn't want to be suspected, you should've lived a good life.

What's this? Did he say he's from Hangzhou?

Maybe he used ruthless methods there, sucking people dry, and wanted to start fresh in this remote countryside.

Tsk. Well, what can you do?

Whether it's laundering the past or whatever, you can't harm someone who's running a legitimate business now.

I'd love to chop him into a thousand pieces, but what about the people smiling here?

"Good. This is an ideal workplace. As long as you keep it like this, there won't be any bloodshed."

"Anything else you'd like to say?"

"Not really."

"Like an apology or how you feel?"

"Not at all."

I know what you're expecting, but of course, Qing isn't sorry at all.

In fact, she's being merciful by letting it go. A hundred and eight bows of gratitude wouldn't be enough.

"Then, you've finished your business. I'd like to rest now."

"Is the sun setting? Ah, I'm hungry."

"I'd like to rest."

"No, who's begging for food? Even if you offered, I'd refuse. Let's go eat, guys."

Who would eat food that might be tampered with?

There's no desire to eat a meal laced with someone else's saliva. Even if you offered, we'd refuse.

And so, Qing left the Zheng Family Estate behind.

With her superhuman hearing, she caught the words from behind.

-Damn it, what bad luck. Hey, go sprinkle a box of salt. No, no, better yet, shake out a whole sack. Maybe we need to perform an exorcism, damn it.

After all, curses are the highest form of praise.

Qing hummed a tune as she walked.

However.

While Qing saw the world differently, reading people's karma as numbers, and felt utterly refreshed.

Her friends did not.

Peng Daesan and Zhuge Lixian exchanged glances, silently shaking their heads.

But the surprising thing was the reaction of only two in the group.

That's because Jian Buxi had no thoughts.

Because she has no thoughts at all.

And Xue Iri also had no thoughts.

Because, again, she has no thoughts at all.

Ciyu is still young.

And Tang Lan-Ah couldn't find a single fault in Qing's attitude. In fact, she was even more impressed.

\textit{She even used honorifics with a lowly merchant. Qing is too kind for her own good.}

\textit{That's why the merchant, not knowing his place, dared to act rudely, thinking she was an easy target.}

\textit{Being kind is good, but Qing needs to be a bit more ruthless.}

If Qing becomes any more ruthless, what kind of three-headed, six-armed monster will be born? It's a scary thought.

Anyway, this is the reality of the future of Wulin's greatest friendship group, the Half-Sword Double-Saber Association!

If anyone knew, they'd sigh deeply.

'The future of the Orthodox Wulin, is it really okay?'
