\chapter{Our Wish is Slaughter (2)}

Qing felt as if she had been dealt a harsh blow.

In professional terms, it was a preemptive strike—sharp, precise, and executed with the utmost sincerity. It was a painful hit for Qing, who hadn't even drawn her sword yet. But.

Qing steeled herself as she observed the despicable deeds of the human trafficker.

There was no turning back now.

For the sake of justice in Wulin and the visceral satisfaction of eradicating evil, she would walk the path of ruthless righteousness.

Swoosh—the Moonlight Sword slid out with a cold, metallic sound.

She had gathered the necessary information, and the villain's crimes were undeniable. She could enjoy this—no, she would deal with this scoundrel first and think later.

"Come forth, you've confessed your sins! Pay for your crimes with your life!"

"Wait, what crimes? What have I done wrong? This is unjust!"

"What? Didn't you just confess with your own mouth? How could you buy and sell people? Isn't that what you brokers do? I can't forgive this!"

"Brokers? This is a misunderstanding! We're nothing like those human scum! It's all a misunderstanding!"

"Ha, now it's a misunderstanding? Are you trying to mock me? Adding the crime of disrespect—death sentence!"

"Wait! We're not brokers, we're just… charitable businessmen!"

"Huh…?"

Qing paused, her sword halfway drawn.

"Charitable?"

"Yes. We provide opportunities for those who have fallen through the cracks of society to rise again. We help them find jobs and, in the process, take a modest fee. You could say we're intermediaries for personal rehabilitation."

"What kind of nonsense is this?"

"As the saying goes, 'Man proposes, but Heaven disposes.' Isn't it too cruel to leave those who've failed to fate? And what if they face insurmountable trials or need large sums of money? Should those without money just give up and die? But! As long as they're healthy, there's nothing they can't achieve. We're here to support them."

"So, you're luring desperate people into slavery?"

"Slavery? No, it's a contractual agreement."

The man with a scarred face and disheveled hair spoke with eloquence.

Qing's thoughts came to a halt.

You shouldn't judge people by their appearance, but what? What is this?

At that moment, a sharp whistle pierced the air.

"What's going on here?"

The sound of a flute echoed, and a group of martial artists wielding six-foot staffs swarmed in from all directions.

Qing, holding her sword, watched as one of them approached.

Instantly, a murderous glint returned to her eyes.

Wasn't it said that causing trouble in Heukshi would provoke an attack from the Black Point martial artists?

If they attacked first, wouldn't it be self-defense?

Surely, they'd come with an arrogant attitude, threatening her with death if she didn't back down.

If she pretended to falter, they'd demand compensation or even a limb as humiliation.

Then, without further ado, wouldn't it be time for the sword to speak?

Qing swallowed hard.

The Heukshi martial artist bowed to her.

"My apologies, honored guest. Is there a dispute with our member merchant? If there's an issue, could you please explain?"

"What? Why are you doing this? What's going on?"

Qing shouted in frustration.

The Heukshi martial artist's attitude was respectful.

Instead, he turned a stern gaze toward the broker, his voice sharp.

"Hey, Mr. Jang, what's going on here? Why is our guest so upset?"

"It's, it's not like that. There seems to be some misunderstanding. She was inquiring about the whereabouts of our clients, and, well, it seems she has a grudge against brokers…"

"Ah, I see. Honored guest, we strictly prohibit any coercive transactions in Heukshi. Could you tell us where we've caused you discomfort?"

"But, you're brokers, aren't you? Human traffickers who make a living off this—how can you—"

Qing's indignant voice was cut off by a hand on her shoulder.

She turned to see Peng Daesan's hat swaying from side to side.

"Enough. Let's, uh, think about this."

"What? Did I do something wrong? Is it so bad to want to cut down some villains?"

"Sister, that's a bit…"

Even Zhuge Lixian shook his head subtly.

Qing looked around at her companions.

Tang Lan-Ah seemed to be avoiding eye contact, while Xue Iri and Jian Poxi looked completely indifferent.

"Honored guest, please calm down. Have a cup of tea, and we'll investigate the matter you've brought to our attention."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the reception room of Heukshi—a place fittingly named for welcoming guests—tea and shiny, honey-glazed pastries were laid out on the table.

Normally, Qing would have vented her frustration by devouring the pastries like they were the flesh of her enemies.

But this was Heukshi—who knew what was in them?

So, with her anger still simmering, Qing let out a bitter laugh.

Why is this happening to me?

What did I even want?

Just to cut down those who deserve to die, those whose deaths would benefit the world.

Is Heaven so indifferent that it treats me like this?

How many villains have I sent to hell? Instead of supporting me, why are they making me out to be the bad guy?

At that moment, a middle-aged man with a sharp, greedy face entered the tent.

He was the epitome of a corrupt merchant—anyone could tell at a glance.

Qing's eyes lit up with a glimmer of hope.

Could this be it?

"Ah, my apologies. Is the tea not to your liking? It's not the finest, but it's Yunnan Pu'er. I am Chang Zhengwu, the owner of Heukshi."

Hmm, unnecessarily polite again.

Qing's shoulders slumped.

"It seems there was an issue with our labor intermediary, Mr. Jang. From our investigation, it's not a significant problem."

Qing's eyes flashed again.

This guy is saying it's not a problem?

He hired a quack to lure desperate families into selling themselves, and this wasn't just a one-time thing. Where did all those people go? What are they being used for? It's unimaginable.

When Qing pressed him, Chang Zhengwu shook his head.

"Ahem. I understand your concerns, but was there any coercion in the process of convincing the patients' families? For example, threats of violence?"

Like holding a sword to their heads and forcing them to sell themselves.

Well, no, that didn't happen.

"Of course, the group that provided the medicine is suspicious. But they bought the goods and paid the price—isn't that fair?"

"But they set the price at ten gold pieces. How many patients can afford that? It's practically forcing them to sell themselves."

"But if they're willing to pay that price, isn't it because they need it? Perhaps the ingredients are expensive, or the process is painful, or it requires a lot of labor to justify the cost."

"…"

"And our labor intermediary is not a broker. He only takes a modest fee for introducing jobs. In the case of Physician Tae, he had already agreed with the Zheng Family Estate to take all the workers he recruited. So, Mr. Jang was merely facilitating the transfer of workers. That's what I've heard."

"But what is the Zheng Family Estate doing with all those people? Isn't it obvious that something shady is going on?"

"They're probably using them to establish new tea plantations. Tea farming is labor-intensive. Have you seen how tea plantations operate? The entire mountainside is covered with tea bushes, with no shade in sight. To clear the jungle and establish a plantation, it's not a job for a small group of people."

"Hmm."

Suddenly, the idea of clearing a mountain brought to mind the horrifying concept of slash-and-burn agriculture.

Such work would require slaves—who else would do it?

But using human trafficking for slash-and-burn? What kind of monstrous, inhumane scoundrels would do that?

"Besides, why would a merchant care about what the customer does with their purchase? Does a butcher ask what dish the meat will be used for or who will eat it before selling it?"

His words flowed like a clear stream.

But who was Qing?

She was the Heavenly Flower Sword, the most eloquent and terrifying mouth in Wulin.

She could hold her own in a war of words.

On the way here, she saw vendors selling poisons, drugs, stolen goods, and even swords. Who would buy these things without ill intentions?

Hiding behind the so-called "merchant's code" and claiming not to care about the customer's intentions was just irresponsible sophistry.

If someone buys a mask, a sword, and a corpse-dissolving potion, their intentions are pretty clear.

Saying "we just sell what the customer wants" doesn't absolve them of being accomplices in a broader sense.

But Qing simply let out a deep sigh.

So, is that a crime worthy of death?

It doesn't seem that extreme…

Then, if there's no blood to be shed, why waste the effort?

So, instead of pointing this out, Qing decided to address the injustice she felt.

"That aside, I heard the people were sent to the Zheng Family Estate in Gaeguhyeon. Can I trust that information? Can a merchant just blurt out customer details like that?"

If the broker had tried to hide it, she could have had her fight.

But he just spilled everything without being asked.

"From my perspective, isn't it true that even the most successful business can collapse overnight if it doesn't uphold its principles? Heukshi fell because it lost the trust of its customers. When a merchant loses the people's favor, no one helps, and they just spit on its downfall."

"Huh? Heukshi fell?"

"It's not surprising, given how many people were wronged there. The place was full of counterfeits, coercion, and threats—was it a market or a den of bandits? So, even small merchants like me got a chance. Black markets will always exist, but it's better to have them gathered in one place. That's what the higher-ups thought."

But they didn't want to repeat Heukshi's mistakes, so they aimed for strict quality control and customer-first policies.

Thus, Heukshi was born.

"What does that have to do with leaking customer information? If you're customer-first, shouldn't you keep such information confidential?"

"If someone's asking for that information, it must mean there's a big problem caused by our transactions. We can't take responsibility for the customer's mistakes. Take you, for example. You drew your sword so confidently—you must be a high-level martial artist, right? How could a mere black market handle you?"

"Hmm."

"So, it's better to be upfront. If customers know we'll reveal everything, those with shady intentions won't even come here. It's a way to filter out bad customers from the start."

It was a survival strategy for the powerless.

Shifting responsibility as much as possible.

And since there was no secrecy, those with ulterior motives wouldn't even try.

Of course, such secrecy usually comes at a high cost, and those with shady dealings are often big spenders.

But they chose to prioritize safety over profit.

Hmm, clever, I guess.

He doesn't look it, but he managed to come up with this…

Of course, it wasn't Chang Zhengwu's idea.

Unbeknownst to Qing, he had copied the methods of the Bai Dian, a group currently dominating the black market.

The Bai Dian's roots—its parent company, in Qing's homeland's terms—hadn't yet extended its influence to the southern regions, so local imitations were popping up.

But Qing had no reason to know about this innovative, customer-friendly black market.

Instead, she let out a deep sigh.

\textit{How can I trust these people who spill everything so easily?}

\textit{Maybe they really do need slaves for tea plantations.}

\textit{Or, if there's some conspiracy, they wouldn't use such an obvious method.}

\textit{My slaughter…}

\textit{Our wish is slaughter, our dream is slaughter, the slaughter that saves lives. But cutting down villains is so hard.}

\textit{How am I, a kind and virtuous killer, supposed to live like this?}

\textit{This is just too much…}

\textit{I still need to get the prescription, so I'll have to go, but, hmm, my energy's drained.}

Qing's shoulders slumped in defeat.
