\chapter{Friend (8)}

If A-Qing had majored in science and engineering or arts and physical education, she would have gone mad, tormented between the urge to slaughter everyone and the sin of it.

But since A-Qing specialized in the humanities and social sciences, she was living well, only receiving the connotative impacts when related to liberal arts!

However, had she majored in medical science or law, she wouldn't have even had the leisure to consider gaming as a hobby.

If that was the case, then there was no reason to suffer in the first pl-

No, forget it. Anyway, this was why people should learn.

After all, the saying, Knowledge Is Power by France Is Bacon \footnote{Francis Bacon, an English philosopher} was that very principle.

'Bad people aren't human, so there's no need to treat them as such. Mencius said so. So, come on. Fight me, you dumbass. It's only fun for the hunter when the beast fights back.'

Nogal swallowed a sigh internally.

\textit{Shit, I got involved with an actual crazy bitch!}

It was exactly the kind of idea one would expect from a devilish homicide, second to none.

Nogal pondered how he could get away alive.

Escape was impossible. There was no hope in it.

The opponent possessed peerless Movement Techniques and could even strike from a distance with her Air Palm.

Even the act of running away itself posed a problem.

If a guard fled, leaving their charge behind, they would be pursued until death.

After all, the Black Shadow Association Leader would never forgive a guard who abandoned his daughter.

And undoubtedly, his wife and ten-year-old son would also meet a tragic fate.

As such, the only options were to defeat her or rely on her mercy.

In the face of a life-threatening crisis, the brain exhibited unprecedented focus.

It was why martial arts would break through walls and reach new heights during life-and-death battles.

Finally, Nogals brain found the most rational path among countless futures.

Masters often showed a peculiar leniency.

Like, 'Oh my, your loyalty is truly admirable!', or something similar.

Of course, the chances of that were one in a million.

But if he was going to die anyway, he had to at least save his wife and son.

The Black Shadow Association Leader, though a part of the Unorthodox Faction, was still someone who would take care of the family of a guard who sacrificed their life for his daughter.

Nogal steeled himself for this resolute decision.

"I shall offer my life to atone for my sins to you, Exalted Lady. Please, could you end this grudge with just me?"

Sadly, A-Qing had already surpassed her threshold of thirst.

It had been far too peaceful lately and the absence of a real fight had ignited her bloodlust.

"Nah, don't want to."

As such, her hand moved on its own.

Her slender fingers slashed Nogals throat from right to left.

The fingers were one of the most sensitive parts of the body.

So sensitive, in fact, that it was able to feel every millisecond of that moment, spanning a blink of an eye, in slow-motion.

The squelch, as it tore through the soft leather of the neck, buried into the muscle, before straining against her strike.

When the elastic blood vessels wrapped around her fingers like rubber bands, the tense resistance intensified further.

And then, it touched the solid Adams apple.

Digging deeper, as if scooping sand, the carotid artery stretched over the shoulder blades, then snapped, unable to withstand the tensile stress any longer.

And it was only then did the slowed time returned to normal.

With a \textit{Slash}, the large artery was torn, spraying blood violently.

The warm, fragrant blood that finally whipped onto her face.

And at the same time, the world erupted in white flames.

{\itshape \bfseries A sticky lightning flashing from the spine to the very extremities of her body.

A majestic ocean of light whispering in the serene universe.

206 bones, tendons, and muscles and 250,000 kilometers of blood vessels swirling before bundling into one.

A garden of flowers blooming hazily amidst blazing flames.

The heart ascended to the head, pulsating through the brain and eardrums.

A choir where ten thousand voices blended in a falsetto harmony.

Salty and sour. A spicy sigh. A single sweet tear.}

And then, she came to, just like how one awoke from sleep.

It was a natural awakening of consciousness, becoming suddenly aware that she was awake.

It was the first time she felt refreshed in this world.

And so was the feeling of revitalization after having a good sleep, without any dissatisfaction in her slumber.

The sense of fulfillment filled her inner self akin to the feeling one would get after watching a movie that ended happily.

But unlike her mind, more healthy than ever before, her physical condition was far from ideal.

For some reason, her arms and legs were trembling, almost as if a full nights sleep would guarantee muscles aches all over her body.

On top of that, what in the world was this?

Her hand felt heavy, so she lifted it. But upon doing so, she saw hair in her grasp and a womans head dangling from it.

"Ah, Lady. When did you end up as just a head? How pitiful."

It seemed like she had lost her senses for a moment.

She couldn't tell how much havoc she had wrecked.

But what was certain was that there wasn't a single part of her body that didn't ache.

A-Qing hurriedly checked the status of her Righteous Karma.

Fortunately, it seemed she regained consciousness after killing just this lady, seeing as how her Righteous Karma had increased a little compared to before.

A-Qing tossed the head away, before scratching her own head and speaking.

{\itshape Phew, was it because its been a while...

Anyway, it was for the best. It all worked out.}

After all, she had accumulated more Righteous Karma and her mood was surprisingly good. Wasn't that good enough as is?    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When she returned to the teahouse, it was bustling with commotion.

The three Young Masters were making a fuss, so A-Qing briefly explained.

"I told you, it couldn't be helped. They said they'd capture me, chop off my limbs, and throw me in the brothel, you know? Obviously, I couldn't just let that happen."

Her tone was as casual as if she was discussing what she had for breakfast.

But the content was grim, stiffening the faces of those who heard.

Moreover, she was entirely drenched in blood; so much so that droplets were dripping off her chin.

"It's fine. Its not my blood, you see."

"Elder Sister, you should wash up first. Excuse me, Owner. Sorry to bother you, but can you prepare some water so she can wash her face?"

Fuck everything else. The owner wished they would just leave. 

Of course, he didn't say that. After all, no one would dare to confront a woman dripping with blood and a muscular giant.

"Wipe it off."

Peng Daesan offered a handkerchief.

She had deliberately covered her entire body with blood, so just one handkerchief wouldn't be enough.

As such, his offer was both touching and commendable, considering how he would have to discard the whole thing after.

"Ah, just keep it. A quick wipe will do. There's plenty over there, you know?"

A-Qing stepped outside the teahouse, picked up a dropped handkerchief, and wiped her face.

After cleaning her face, wringing her hair, and repeating this cycle of picking up and discarding, the moistness was a bit lessened.

Returning to her seat, she was greeted with a water basin, prepared just in time, so she splashed her face cheerfully.

"So, why don't you start speaking now?"

"About what?"

"You said you were going to the lavatory, then you show up like this. And now, you have the audacity to ask about what?"

"What, why? Why are you suddenly angry?"

"Ha, who's angry? Me?"

Peng Daesans reaction was quite sharp.

For reference, ever since starting her Wulin journey, A-Qing had never once held back when facing any kind of aggression.

However, she was in a very good mood right now, so she didn't want to argue and upset each other.

"Wait! Stop the anger!"

"Are you seriously trying to just brush past this by acting like that..."

"Hey you, mister over there! You stop too! If you go over there now and get swept up in this, it's not my responsibility, okay? Remember, what does curiosity do? What does curiosity kill?"

A-Qing shouted towards the back door.

A man, sneaking towards the back, changed his expression as if realizing something and turned back.

A-Qing refocused her attention on the tea table.

"Seriously, I don't know, okay? Calm down. It was just a minor scuffle and I won anyway, you know? I left my sword, so they underestimated me. That's all."

"Is that seriously something you should be speaking about so nonchalantly?"

"I mean, well, it's nothing special. It happens all the time, so..."

It happens all the time, so.

Peng Daesan felt like he had been punched in the guts.

A-Qing was a youthful Master.

And such Masters did not just emerge out of nowhere.

One needed to be born with talent and placed in the right environment to become a Master at such a young age.

For instance, it could be support from their clan.

Or it could be a series of real battles where their life was at stake.

While Peng Daesan was lost in such thoughts, A-Qing snapped her fingers and changed the subject.

"Ah, right. Hey Zhuge, you know martial arts well since youre a Jegal, right?"

Honestly, the two cousins weren't well acquainted with her yet and they couldn't interfere in a relationship between opposite sexes, so they had just been twiddling their thumbs without being able to speak a word.

But thanks to A-Qings change in topic, they found a gap to enter. Thus, Zhuge Ihyeon answered her call.

"Are you talking about martial arts, Elder Sister?"

"Yep. What's the strongest Hand Arts?"

A-Qing recalled the moment she beheaded Nogal.

The sensation of her hand wrapping around it. It was the best.

She had an epiphany for a moment, striking her like lightning.

\textit{Ah. I should learn a Hand Art.}

Despite the unexpected question, Zhuge, who fundamentally could not resist explaining, answered whole-heartedly.

"Elder Sister, originally, it is impossible to immediately answer what the strongest martial art is."

"Why?"

"Because in Wulin, this topic has been debated for thousands of years. In truth, whenever two or more men gather, the conversation inevitably turns to what the strongest martial art is. Without a single exception."

"Then what does Zhuge think?"

"In my opinion, Hand Arts of itself is not really a good martial art."

"Why?"

"Well, Hand Arts is inherently very brutal. If people dislike the sensation of injuring others with just a sword, imagine how much worse it must be to scratch, slice, and tear off flesh with their bare hands. Isn't that so?"

\textit{Isn't that what makes it good?}

A-Qing cocked her head in confusion.

As expected, it seemed the current times did not suit her.

"Can you stop digressing? I asked you which is the strongest."

"About that...Well, fortunately, when it comes to Hand Arts, all martial artists can agree on the strongest. And that very martial art is-"

Zhuge Ihyeon paused with an air of a practiced orator and tried to take a sip of tea.

But right as he was about to do so, he was startled by the sharp glare of Peng Daesan.

It was a gaze telling him to finish quickly.

As such, Zhuge Ihyeon quickly concluded.

"The strongest Hand Arts is the White Hand Demonic Arts."

"White Hand Demonic Arts?"

"Ah! My throat feels so dry, suddenly!"

Zhuge Ihyeon abruptly started doing other things.

A-Qing, knowing the reason, changed her target.

"Hey, why are you demoralizing and bringing down our Zhuge spirits?"

"Is this really the time to leisurely talk about martial arts? After being in that state? Just look at yourself!"

"Well, its because I don't think I'll have the chance to ask if it's not now, you know?"

"...What is that supposed to mean?"

Just because A-Qing never held back didn't mean she intended to act like a mantis stalking a cicada, unaware of the oriole behind.

She knew well enough that, Late-Stage Peak Realm or not, she couldn't face an entire sect alone.

After all, she had been hounded a few times in the past.

"That sect called the Black Shadow Association. Its considered a pretty big one, right?"

"Were they from the Black Shadow Association?"

"Unless they were impersonating."

Peng Daesan wiped his face.

In Luoyang, there were three major forces.

The Chae Clan, the Scarlet Devil Union, and the Black Shadow Association.

The Chae Clan was a prestigious household of Grand Generals that served generation after generation, while the Scarlet Devil Union and Black Shadow Association were sects aligned with the Unorthodox Faction. 

Despite the weakening of the governments power, the Chae Clan still wielded a sword of a general and possessed military authority suitable of that.

They were the actual magistrates who held most of the rights, interests, and privileges in Luoyang. 

The Chae Clan, due to their dignity as a household of Grand Generals, left the shady parts of Luoyang untouched, which were then split between the Scarlet Devil Union and the Black Shadow Association.

"I mean, they boldly attempted human trafficking in broad daylight, after all. I'm sure they weren't ordinary guys."

"You knew that and still laid your hands on them? No, setting that aside, with your skills, was there even any need to get into a brawl?"

The Black Shadow Association wouldn't dare kidnap a Late-Stage Peak Realm martial artist unless they were out of their minds.

It meant that she chose to resolve the issue with bloodshed when just showing her martial prowess would have sufficed.

And A-Qing confidently affirmed that deduction.

"I don't avoid conflicts. And if it's a bad guy who picks a fight, even more so. A real man never runs away."

\textit{Was this woman actually batshit crazy?}

One thought briefly crossed Peng Daesans mind- 

\textit{Shit, I forgot, but she's the same woman who actually hit me after I told her to have a go.}

"Can't you think a little, even if it's just a little, before acting? How do you even plan to deal with the consequences?"

"I gotta dip, obviously."

It meant she was going to run away.

She had just been talking about how real men did this, real men did that and whatever, but now she was saying she would run away.

Peng Daesan felt utterly deflated.

"So you're going to run away? Is that what you're saying?"

"The sight of someones back! Leaving with conviction! Because they know when they must depart! How beautiful is that! Like falling leaves lying scattered!"

"Stop with the nonsense! Can you be serious for once!"

Peng Daesan raised his voice.

A-Qing, in contrast, smiled softly.

\textit{This brat. Look at him talking loudly just because he got a bit fond of me. }

"Sorry. Was it Diaochan Dining? Ill treat you next time we meet."

"If you had just held back a little bit in the first place..."

"Well, its not like we're going to live together for thousands or tens of thousands of years. It's what? A fortnight? After that, were going to part anyway. So, it's not a big deal to part a bit early. And if fate allows, well meet again anyway."

A-Qings words left Peng Daesan utterly speechless.

Now that he thought of it, that was indeed the case.

They had joined the escort convoy to Longcheng separately and would naturally part ways after a few more days either way.

Considering that, wasn't there no reason for him to keep her with him?

Peng Daesan leaned back in his chair. 

A-Qing spoke as she stood up.

"Ah damn, all my luggage is still with the trading company. Oh yeah, let the Escort Leader know that I'm sorry for leaving so suddenly. Also, see you later, Little Supreme Justice and Zhugie."

"Take care of yourself too, Young Lady."

"Yes, Elder Sister. I shall see you next time."

A-Qing stepped out of the teahouse.

Now that she left, there wasn't really anywhere in particular for her to go.

But it wasn't like she had come to Wulin because she had somewhere to go either. Her life was one of going wherever and however it took her.

She'd catch a thief here, a bandit there, and now, she even had a new goal called the White Hand Demonic Arts.

With that thought, A-Qing kicked off the ground and ran off.