\chapter{Friend (5)}

A-Qing lacked common sense, but that didnt mean she was stupid.

She also knew the implications of this shameful trash.

It was the persistent and desperate struggles of women trying to somehow create a connection with the Jade Qilin.

If it was to a certain extent, she would have playfully poked his side, telling him to pick some up out of courtesy. 

However, while A-Qing was inhaling the entire collection of Zhongyuan snacks ---fried pastries, steamed pastries, boiled pastries, baked pastries, and dried pastries--- the littering continued endlessly.

Now, just like Kim Sowol's Azaleas\footnote{Poem made by Kim Sowol}, it was to an extent where she could easily trample on the handkerchiefs laid out step by step without even intending to.

Picking them up one by one would turn her into nothing but a woman gleaning the fields.

A-Qing clicked her tongue.

"Wow. I'm getting sick of it. Seriously."

"I thought you would tell me to pick them up."

"How can someone pick all that up? Sheesh, someones back would bend in half during such an attempt."

A-Qing voiced a question that suddenly occurred to her.

"Do the owners pick these up later?"

"...Of course."

Peng Daesan hesitated.

Did they pick them up again? Wasn't that a bit too unsightly?

But then, would they just leave it like that? Wasn't that too much of a nuisance?

Peng Daesan flinched.

Why was he even thinking about something like this?

"...I am sure they'll send someone later to collect them."

"Really? From there? Is there someone who specializes in retrieving lost items or something? Also, those things get stepped on and kicked around."

The women around Peng Daesan were in a competitive relationship against each other.

While pretending to just pass by, they obscured the view, sneakily dropped items on top of other items, and stepped on their rivals belongings.

"If someone picks them up and sells them, would they make money?"

Peng Daesan doubted his ears.    

"Are you out of your mind?"

"No, like, look at them. Some look pretty expensive. They'd come back for those, wouldnt they?"

A-Qing pointed to a sachet rolling on the ground.

Handkerchiefs were not too difficult to throw away and drop, but they didnt have a great meaning.

One of the ways to quietly convey a breakup to a lover was to gift a white handkerchief.

The minimum requirements to exchange handkerchiefs between lovers would be something like a red fabric embroidered with gold thread or something similarly ornate.

Thus, women from wealthy families dropped norigaes.

Very occasionally, there were women who would drop sachets or buyaos, but other women didn't dare to step on or kick around such precious items.

They feared the consequences of provoking a woman who could afford to use such expensive items as bait.

On the other hand, if there were no consequences to fear, it meant it was fine to provoke.

Just like that person over there.

"What are these? So dirty and messy."

A short boy in clean white clothing appeared, kicking the womens pure intentions scattered on the ground.

A burly titan of a man next to him spoke.

"It is obvious at a glance that they are traces of Senior Brother Jade Qilin, aren't they?"

"Ah. Thats true. Little Brother Peng! Are you here? "

"There is no need to shout, is there? We just need to follow the gaze of the women. Look. He is right over there."

"As expected of Little Brother Zhuge! So very smart! LITTLE! BROTHER! PENG!"

A-Qing checked their Righteous Karma out of habit.

The boy in white was 86.

Ooooh, A-Qing marveled.

It was the highest record among all the martial artists she had seen.

And the burly giant was -19. A passably good guy. 

Righteous Karma was difficult to accumulate.

In contrast, the amount plummeted due to Evil Deeds was tremendous.

After all, martial artists often had times when they had to take lives.

Even if their numbers are inclined to Evil Karma, being in the two digits meant they lived fairly decently without doing too much harm.

A-Qing asked curiously about the unusual combination of the two.

"You know them?"

"Indeed."

Despite his response, his expression was not all that pleased.

However, Peng Daesan had never been seen being affectionate to anyone. In fact, one couldn't even imagine it.

It just seemed to be his natural disposition to be that way.

The boy entered the teahouse while shouting.

Despite his tiny size, his voice was as loud as a train whistle.

"Little Brother Peng! Long time no see! I didn't expect to meet you here! And your face is shining as brightly as it always has! Nice! Very nice!"

"Senior Brother Hwangbo, it has been a while."

"Yeah! When was the last time? Oooooh! What's this?! You're with a woman?! Could it be?"

"Absolutely not. Never."

Peng Daesan looked positively disgusted.

"Haha, that was rude, you know! You need to be more aware of the hearts of women, it seems!"

Peng Daesans mood soured instantly.

Indeed, that was how he should be reacting when someone touches upon his sore spot.

However, Peng Daesan knew this rascal quite well.

He was a kind person with not a hint of malice, as well as being terribly oblivious, so expressing his displeasure would only be a loss to him.

Utterly unaware of his inner thoughts, the boy laughed heartily.

Though it didnt suit him, being that he was so tiny. 

"This individual is Hwangbo Uncheok, just a Senior Brother I know. And that punk is Zhuge Ihyeon."

"Senior Brother Peng, why is one called an individual and the other, a punk?"

"You are indeed a punk. You dragged him here on purpose, didn't you?"

"The women were so thrilled and the streets were so chaotic that it was obvious that Senior Brother Peng had made his move. Of course, I had to greet Senior Brother. "

The tiny kid was Hwangbo Uncheok. Surprisingly, a sweet age of twenty-seven.

He looked like a middle school student from the outside tho.

\textit{This kid? Twenty-seven?}

Seeing A-Qings expression, Peng Daesan added.

"He took the wrong medicine when he was young."

"Ah."

If he ate the wrong kinds of herbal medicine, then there was nothing that could be done.

A-Qing was swiftly convinced.

The Little Supreme Justice, Hwangbo Uncheok.

A famously virtuous individual of Jianghu, he was called the Little Supreme Justice, known for his small stature yet having already reached the status of a Great Expert.

He was renowned for his Late-Stage Peak Realm martial arts, his upright conduct, and a lively, boisterous attitude that did not match his small frame at all.

And the titan, who looked like a living incarnation of muscles, was Zhuge Ihyeon. His age was eighteen, in the flower of his youth. 

"Zhuge? Like Zhuge Liang?"

A-Qing asked; she, too, knew the surname Jegal.

After all, Zhuge Liang was way too famous for her not to know.

But, why? If it was Zhuge, then...you know? Wouldn't they be that family who was fragile in body but brilliant in mind?

"He seems to have received too much of his maternal sides blood."

"Of course! He's the son of our aunt! Its only natural!"

"I am satisfied. It is about time the Zhuge Clan shed its image as frail scholars."

Zhuge Ihyeon flexed his arms and showed off his biceps.

In modern terms, it was the very pose that people called the Front Double Biceps.

The sleeveless robe he wore, uncommon in Zhongyuan, amply revealed his muscles and his pride in them.

The Beastly Sage, Zhuge Ihyeon.

It meant that he had the body of a beast, but a brain of a sage.

A natural genius even among all those Under Heaven, born with the mighty physique of the Hwangbo Clan and the exceptional intelligence of the Zhuge Clan.

His mastery of martial arts might not be the highest, but peoples expectations of the Zhuge Clan were not in that area to begin with.

Conversely, the elders of the family did indeed have expectations in that area.

Among the Five Noble Clans of Zhongyuan, the Zhuge Clan ranked on the lower side when it came to martial studies, but they were still a member of the Five Noble Clans.

However, maybe due to their overly impressive ancestor, people tended to see all those surnamed Zhuge as merely smart nerds.

Honestly, it was an unfair situation, much to their chagrin.

Zhuge Liang was a man of steel-like stamina, enduring a heavy workload, including night shifts, for 11 years after the death of Liu Bei. 

This feeling of injustice turned into resentment, leading the Zhuge Clan to focus more on improving their constitution than actually strategic marriages.

But the result was always the body of a sage and the brain of a beast.

It was so bad that they even seriously considered whether some sort of curse had been cast, thus studying their bloodline with means of sorcery.

Amidst this, the appearance of Zhuge Ihyeon, showing both muscles and brilliance from a young age, was a great celebration for the family.

These were unwelcome guests from Peng Daesan's perspective.

He tended to shy away from peers with cool titles. Little Supreme Justice, Beastly Sage. But then suddenly, Jade Qilin?    

And then there was Hwangbo Uncheck; the person itself was...How to put it?

A good person? But only a good person? 

He had a somewhat pure brain and absolutely no tact whatsoever.

On top of that, he could never tolerate injustice.

He even confronted Transcendent Realm Masters over injustice. 

Had that Master not generously laughed and praised him, he would have long been deceased.

That was when the title Little Supreme Justice was born.

To put things simply, Hwangbo Uncheok was tiring to be with.

And though Zhuge Ihyeon was quite a decent guy, the fact that he was always around Hwangbo Uncheok was his fatal flaw.

After all, the Little Supreme Justice's love for his cousin was famous.

"How did you end up with our Little Brother Peng, Young Lady?"

"I happened to be accompanying him on the same escort convoy."

"Our Little Brother is particularly prickly to women, though. Could it be..."

"We're just friends. Friends. Same-age friends."

"Oho. Where would friends exist in the relationships between men and women?"

"Right here?"

"It always starts like that. Then affection grows as they stick together, thus becoming lovers, and then spouses. Isn't that so?"

There was a certain familiar smell in this unfamiliar Zhongyuan.

The manner of emphasizing our.

The attitude of trying somehow to tie the entangled woman to a Little Brother who apparently had no interest in women at all. 

'Yo, our youngest. Why did Choi Nayeon from C Line give you coffee? Doesn't this look like its a step away from having beef soup together?'

'That's nonsense. She just gave it to me as a thank-you for giving her a ride yesterday.'

'Oooooh, our youngest. Are you already at the stage where you two take the same car together?'

'Come on, it was raining yesterday. She missed her bus, so I just gave her a ride since I've seen her face a couple of times.;

'Our youngest is quite the player, huh? Truly, a rizzler. That's right, thats right. That's how everyone should make their move.'

'I'm telling you thats not it.'

'Look at our youngest. Always refusing to leave his house because he said he was playing games or whatever. He's all grown up now!'

He was a senior who had entered the same work line a year earlier.

Not long after, he confessed to Oh Haeun from C Line, got brutally rejected, and left the company.

He was definitely not a bad person.

He was the kind of person who'd drag you to a company dinner (but it was actually a drinking party with voluntary attendance, something never missed by married men), saying he'd cover your share if you didn't want to go.

After seeing a newcomer become isolated for not attending one company dinner, I realized that his insistence was actually a kind gesture worthy of thanks. 

H'ed even visit occasionally after resigning to treat me to a meal.

But spreading rumors linking me with Choi Nayoen, as if pushing us together like Cupid, was a bit much.

A-Qing recalled the past.

\textit{Fool me once, shame on you. Fool me twice, shame on me.}
