\chapter{Friend (4)}

The beauty standards in Zhongyuan were not much different from the modern era.

Báizhū fēngxíng,: a white face and an ample bosom.

Xìyāo qīngyíng: a slender waist and a light body.

Ōubā shànbīn: long raven hair.

Míngmó yóubān: clear eyes with distinct black and white pupils.

Dānsūn huòqí: red lips and white teeth.

Among these, there were priorities, with the most important being a small and slim figure.

In modern terms, it was the near fanatical preference of slender bodies.

A preference for slender figures who were short, at that.

However, that did not mean they could have a flat chest.

They had to be well-rounded, full breasts.

And of course, this, too, must be a moderate size.

Ideally about the size of two adult male fists. 

Anything larger was considered vulgar, a characteristic more expected of concubines than main wives.

Hence, men often spent more time with their concubines; it was a society where one couldn't even openly praise what they truly enjoyed.

Ultimately, a beauty in Zhongyuan was the same as a beauty of the modern era.

Or to be more precise, modern beauty standards included those of Zhongyuan.

And then, the Most Handsome Man Under the Heavens, the Jade Qilin, arrived in Luoyang.

People who saw his face, which was as clean as jade and as gracious as the rumors suggested, spread the news quickly, saying 'I saw him, did you see him, I also saw him'.

The most eligible bachelor in all Zhongyuan had made his descent upon these lands!

The beauties of Luoyang all gathered in one place.

And the scene that such beauties saw was-

A cheap-looking, under-developed, whore-like bitch daring to flirt with the oh so noble Jade Qilin.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A-Qing created her character just as written in the recommendation post.

In Wulin Chronicles: A Tale of Life and Death, one's Stats by familiarizing themselves with martial arts; furthermore, any and all martial arts in the game could be learned.

As such, initial Stats were meaningless when entering the later parts of the game.

A-Qing took out all Appearance Stats and invested every one of them into Stamina and Strength.

It was a build meant for an easier start.

As such, when A-Qing first emerged in Wulin, she was literally the Ugliest Woman Under Heaven.

But as she learned and attained more martial arts that belonged in the Fairy Arts Subclass, her Appearance Stat increased significantly.

The 3 types of Yue Maiden (True Form Origin) belonged to the Fairy Arts, and being a Purple Martial Art, it significantly increased the Stats.

So now, A-Qing wasn't ugly.

But that didn't mean she was particularly beautiful either.

She was just average.

Yet, she was stuck right next to Jade Qilin.

It was a stark contrast, the very embodiment of the Relative Squid Theory.

The cheap robes bought for its cost-effectiveness was the very epitome of such a theory's proof.

Hostile glances swarmed in all at once.

However, the real form of A-Qing was a single gamer working in production.

She had no particular complaints about that lifestyle.

Her only wish was perhaps for all those born with a silver-spoon to die.

A single gamer working in production.

To her, romance was nothing more than tiresome emotional labor.

And even when ladies, all dolled up, glared at her with venom, she could casually smile it off with a slickness that came with experience.

With enough wealth to live comfortably alone and hobbies to keep herself entertained, marriage was not even a consideration for her in the first place.

As a result, A-Qing did not pay much attention to the hostile glares confronting her at the gate.

She just whistled at the sudden unfolding of Luoyang's greatest beauty contest.

As she knew that Luoyang wasn't the Land of the Amazon's, she could at least understand why they had all gathered here.

A-Qing nudged Peng Daesans side with her elbow.

"Ooooh. San. Look at your face being worth a pretty penny, huh?"

"It is merely bothersome."

"'Iv wis verely vothersoem'. Oooooh, look at our San! What a sick guy! So cool! A cold-hearted man! But you'd be warm to your woman, right? Kyah-!"

A-Qings words touched on Peng Daesans sore spot in a very ambiguous way.

It was fine. All he needed to do was brush it off.

Normally, he would have frowned upon such words, but strangely, he wasn't offended. Why was that?

Peng Daesan pondered for a moment.

Well, it was because A-Qing's words and actions were akin to the friendly banter and pranks of fellow men.

In truth, men also liked good-looking men.

Though one might think, 'Damn that motherfuckers face is on another fucking level, shit', the underlying feeling was usually just admiration.

The people men disliked weren't the good-looking ones.

The hated were more the type of men who drove Benz in their early-20s or the silver-spoon business owners who strutted around with arrogance.

"Just now-"

"So, if we're in Luoyang, we have to go somewhere! Where are the hottest places? We can't eat dinner when it's still bright out, right?"

Peng Daesan was about to ask something, but A-Qing's words, slipping through that gap like a ghost, made him forget all about it.

It didn't seem like an important question anyway, so Peng Daesan just let it slide.

"White Horse Temple. Or Longmen Grottoes."

"A temple and a cave, huh? Wouldn't the cave be better?"

Peng Daesan didn't hide his disdain, looking at her as if finding her pathetic.

"What the? Why?"

"The only person in the entire world to refer to White Horse Temple and Longmen Grottoes as just a temple and a cave is most likely you."

"So? Ain't it a temple? Ain't it a cave?"

"Do not say such things in Luoyang. The people here are absolutely insane when it comes to their pride in their city. It will lead to them wielding swords."

Surprisingly, that was the truth.

"Can't help it then. Shall we go to Longmen Grottoes?"

"...Longmen Grottoes is far."

"How far?"

"It's quite a distance beyond the Southern Gate."

A-Qing also thought that was too far.

"But there seems to be nothing to see at the temple-"

"If there is nothing to see, then let us just go back."

"Are you seriously going to be like this? Buddy, can't you show a bit more enthusiasm?"

"Such a thing never existed in the first place."

"Let's go. White Horse Temple. You ready, San?"

"..."

"Ugh, you never know how to go with the flow, do you? 'Ov vourse vot. Qvinq'"

A-Qing imitated someone from behind by lowering her voice.

Peng Daesan let out a deep sigh.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Personal tourism tendencies varied greatly, but they could be divided into several types.    

First, there were the planners.

Those who organized every detail of the trip and moved according to a pre-arranged plan.

The slightly lax planners were considered the best travel buddies, overwhelmingly enhancing the satisfaction of the trip.

However, there were instances of planners with superhuman capacities who planned every ten minutes.

It was necessary to be wary of such types; one might end up seeing and doing a lot, but with no memorable experiences left after the trip. 

Then, there were the hermits.

For hermits, traveling was just not working and staying somewhere far from home for a few days. 

Their satisfaction came from not having to go to work and not being at home, instead of delicious, interesting, or famous things.

Comfort was what hermits seeked.

If they felt even a tiny bit tired, they tended to hole themselves in their room.

They often clashed with the wanderer types, thus arguing.

'Why come here if youre going to do this I came to rest, not to suffer.'

Then, there were the wanderers.

They simply loved to roam around.

They meshed well with planners and were best off traveling separately from hermits to avoid ruining friendships.

They ate well and enjoyed everything heartily.

However, once they lost interest, their concentration and motivation would dwindle, thus quickly seeking to leave.

They were the sort who perceived tourism as akin to an arduous journey.

Aside from those, there were the ultimate travel buddies. The silver-spoons. The wealthy ones.

There was a type who one should perhaps not seek companionship with on travels, but since they tended to stick to their own kind, it resulted in little interaction with those outside their group anyway.

A-Qing was one of the wanderer types.

To be more precise, she belonged to the subset of wanderers who loved to eat.

Any time she saw food, shed shoot longing glances at Peng Daesan.

Basically, she was fully collecting her share of the friendship fee, so to speak.

From Peng Daesan's perspective, the amount was pathetic and virtually negligible ---barely pocket change--- but the joy of providing for her was there. After all, it was fun to see A-Qing heartily enjoy whatever she ate.

However, A-Qings impression of White Horse Temple was somewhat ambiguous.

To her, the temple was somewhat? like a red Gyeongbokgung, a familiar sight for her.

A big red Bulguksa, minus the Seokguram Grotto.

She had neither the eye nor the interest in the essence of contemporary Buddhist art, so the only thing worth seeing was the Qiyun Pagoda.

At least she enjoyed seeing the pagoda.

Then, true to her wanderer nature, she quickly lost interest.

When they stepped outside, the time was a bit iffy. After all, it was too early to go straight to dinner.

Peng Daesan grabbed A-Qing, who was about to wander around again, and steered her to a teahouse.

A characteristic of the silver-spoon types was to solve everything with money while strictly avoiding any and all hassles.

Peng Daesan was already tired from walking around for about an hour. As such, he figured that making A-Qing sit and continuously feeding her something, anything might make things a bit more comfortable.

And that worked.

After he ordered a bunch of snacks and seated A-Qing where the outside view could clearly be seen, she became quiet, engrossed in eating and spectating.

Content with this situation, Peng Daesan became lost in thought.

The escort convoy would continue to Longcheng and about five days from there laid Mount Hua, Peng Daesan's destination.

The Absolute Sword Wall of Mount Hua had opened.    

The respect for the penultimate generations zenith, the Celestial Martial Emperor, was due to his genuine love for Wulin.

So much so that the attack on the Imperial Palace was also a warning to the Imperial Family, who were wielding Wulin to embark on northern conquests. 

His affection for the Nine Sects was especially extraordinary.

Thus, he directly imparted one of his teachings to each of them, though as always, the Celestial Martial Emperors methods were somewhat extreme.

After splitting a cliff with a single sword strike, he engraved nine Sword Marks. It was a kind of Insight left by the Celestial Martial Emperor.

The teachings were received by only the Nine Sects.

Neither the One Union nor the Five Noble Clans were included.

The Celestial Martial Emperors disdain for the Beggars Union was well-known, ironically deeming them as even lesser than actual beggars.

As for the Five Noble Clans, he was simply not interested.

He just left a few words, saying prioritizing family over the greater cause was'nt necessarily wrong.

The Celestial Martial Emperors Insights were shared amicably only among the Nine Sects One Union.

He, the Celestial Martial Emperor, was direct and outspoken.

If he wanted his Insights to be public, he would have simply said so. But he didn't'

In essence, it meant 'Do as you please'.

In such a situation, letters were sent flying to the Noble Clans.

The contents roughly consisted of unity blah blah, great cause blah blah, and leading the next generation of Jianghu, thus offering to make the Absolute Sword Wall open to them.

Two things could be taken away from this.

The first was that mere Peak Realm martial artists staring at the Absolute Sword Walls Insights would gain little.

It could be inferred by how the known number of Masters in Mount Hua, whether in the past or present, did not change that much.

The second was that Mount Hua now needed significant help.

There was no free lunch in the world.

One would have to pay the prices to witness the Celestial Martial Emperors Insight.

But what could that price be?

Especially if it was an incident requiring help not just from the Nine Sects, but from the Wulin Noble Clans as well.

Right as Peng Daesan continued to rack his brain.

"San. Look at this for a moment."

When A-Qing called Peng Daesan 'San', it usually meant she really wanted something.

He was gradually understanding the principles of her actions.

A-Qing tapped the empty porcelain plate.

"What is it?"

"I remember someone telling me. That its rude to leave a plate empty, you see?"

A-Qing tapped the plate, urging him.

Peng Daesan was reminded of Heigou.

Heigou was a lion-dog\footnote{tibetan mastiff} reaching up to Peng Daesan's waist.

When hungry, it would bring its bowl and fiddle with it using its front paws.

Even though someone else was tasked with feeding it, the clever animal always sought out him.

"You are quite shamelessly bold, aren't you?"

"Friendship fee."

A-Qing puffed up her chest with an assertive attitude.

Her needless confidence mirrored that of Heigou; a demeanor that expected Peng Daesan to feed her, as if it was only natural for him to.

"But is illegal dumping a trend in Luoyang nowaday?"

"That can't be."

"Then why are those thrown away like that?"

In front of the teahouse, the street was a scene of rampant illegal dumping.

"Colorful handkerchiefs, sachets, and occasionally shoes or even underwear adorned the stone pavement.

It was the very definition of pretty trash.

A-Qing marveled.