\chapter{Friend (7)}

Qing blinked her eyes.

"Ridicule you? Me?"

"How dare you! How dare you!"

Seeing her trembling eyes, she seemed genuinely furious.

A-Qing tilted her head in confusion.

{\itshape What the hell? Why is she so angry?

Perhaps...Could it be that the outhouse was that filthy?}

"After swallowing my money, how dare you shamelessly flirt with him again, as if to rub it in my face! With such a vulgar display! How dare you!"

"Flirt? Me?"

"How dare someone lowly like you approach Young Master Jade Qilin! How dare you!"

Ah. Oh my.

A-Qing finally realized her misunderstanding.

It wasn't a sign of sincerity and favor for the fast-pass to the restroom, but an envelope from a chaebols mother-in-law.

Moreover, it was such a modest amount when considering what her intentions were!

So, naturally, A-Qing felt wronged.

How could a proud Korean man ever imagine receiving an envelope of money after parting ways with his significant other!

If someone was able to, it was an ability to conceive possibilities beyond the realm of imagination. A different fucking stratosphere, so to speak.

If A-Qing had such an ability, she wouldn't have been a production worker but a genius scientist cooking up fucking superconductors.

"First, lets confirm one thing. Are you personally acquainted with Jade Qilin?"

"Oh, look at this? Now you reveal your true colors?"

"Ah. One-sided love? So you're not acquaintances?"

Then, there was no need to exchange any more words with her.

A-Qing slowly started turning on the engine of her mouth.

"Well, fine. Let's say you were ridiculed. Hypothetically. What are you going to do about it, huh? What can you, Lady? What? Shake and scream?"

The womans fierce face turned even fiercer.

"Nogal, Makgwi. Drag that bitch right to my feet. "

The thugs standing beside her, left and right, stepped forward.

A-Qing quickly intervened.

"Wait!"

Now you beg for forgiveness? You should have listened when I was speaking nicely."

"Yeah, okay whatever. Setting that aside. What's your plan? After these ugly misters make me kneel, then what?"

"I'll sever your limbs and toss you into the brothel. You'll be sold for a single coin. If you serve a hundred men a day, well...I wonder how long you can last?"

\begin{quote}
[Sudden Mission Occurrence: Between Innocence and Jealousy]

Description: [You have received a grave insult.]

Actions for additional Free Practice Points:

Righteous Karma) Kill the woman and her two guards

Righteous Karma) Bury the sins of the Black Shadow Association

Righteous Karma) Massacre the entire Black Shadow Association

Heavenly Slaughtering Star) Massacre the entire Black Shadow Association
\medskip

[Sudden Mission Occurrence: Rescue the Women]

Description: [You have learned of the Black Shadow Associations wicked business]

Actions for additional Free Practice Points:

Righteous Karma) Find and rescue the women from the Black Shadow Associations business sites

Righteous Karma) Kill the Black Shadow Association members at the business sites

Evil Karma) Trade with the Black Shadow Association to provide them with women

Heavenly Slaughtering Star) Kill everyone at the Black Shadow Associations business sites

\end{quote}

A-Qing read the lines floating before her eyes.

And then smiled brightly.

The lonely star of Heavenly Slaughter shone with the most irreverent color in the world.

\textit{Yeah, thats right. I did think it had been way too peaceful until now.}

"As far as I know, San might have a prickly side, but he's not a bad kid. So wouldn't a bitch like you never have had a chance in the first place?"

"What did you say?"

"Well, I mean... His family is well off. Even if he's not as good as me, he's pretty decent at martial arts. His face, fuiyohhh, well, there's no need to talk about his face. It's pretty self-explanatory. I guess his character is a bit off, so he's not really capable of being magnanimous. Well anyway, he's a pretty good catch. So why would a guy like him mingle with a bitch like you whose sandwiched between two thugs?"

"You, what did you just sa-"

"Even if the world turns upside down and Heaven and Earth switch their axes, there would still be no chance. Yet, you're seriously following him? Moreover, you're acting like a mother-in-law, telling him to break up or not meet with this girl and shit like that? Hey. That's \texttt{stalking}. It's a filthy crime, you hear me? Ah, you don't know English, do you? \texttt{D o  y o u  k n o w  E n g l i s h}?"

The womans face burned red.

It was so bad, she could literally be called an entirely different species. Perhaps the Red Human race or something.

"If I were San, even if everyone else in the entire world died and only the two of us were left, I still wouldn't peg you. I'd rather do it with a tree hole."

"W-What! You piece of shit, fuck, f-fucking bitch. WHAT ARE YOU DOING, STILL STANDING THERE!"

The woman was at a loss for words in her extreme anger.

Nogal (right) and Makwgi (left) stomped off the ground at her sharp cry.

\textit{That's right. This is what I'm talking about.}

With a wicked smile that seemed to tear her mouth to her very ears, A-Qing shouted boldly.

"Come! My Moonlight Sword is thirs...Ah, shit."

A-Qings hand brushed through the empty air at her waist.

The Moonlight Sword (No. 6) was resting nicely next to the tea table.

Because of that, she missed the moment to counterattack.

Instead, A-Qing briskly jumped back to create distance.

Yue Maiden Footwork.

The following was the contents recorded in the historical texts of the late Spring and Autumn Period.

\begin{quote}
The Yue Maiden moved with the innocent motion of a child, frolicking as if in water.

Yet, she was not slow but as quick as dandelion seeds in a gale, imperceptible to the eye. Despite this speed, she never lost her grace, still as lovable as a young girl.

With one step backwards, she leapt one zhang \footnote{Chinese unit of length, about 3.2 meters}; with the second step, she surpassed two zhangs; and with a light third step, she was suddenly three zhangs away.

Then, unexpectedly, in her fourth step, she would close the distance almost instantly to her opponent.
\end{quote}

After having missed the initiative, A-Qing seized it right back with just one Movement Technique.

This was the reason why Wulin emphasized the importance of Qinggong\footnote{lightness skill}.

The corresponding symbol, ∊ , was a mathematical symbol which signified that Qinggog was part of a broader category that was Movement Techniques.

"What the!"

Nogal was a guard for the Black Shadow Association Leaders only daughter among many sons.

She was so treasured as the youngest daughter after four sons that she even had a Late-Stage First-Rate Expert as her protector.

And such an expert was capable enough to recognize the absurdity of A-Qing's Movement Technique.

Quick Movement Techniques struggled with sudden direction changes while those unpredictable in direction tended to have issues with speed.

Being able to reverse the direction of her inertia in a single step was enough for the Movement Technique to earn vast praise and admiration.

Just being able to maintain the same speed while moving in the opposite direction was enough to be considered a lofty and masterful Movement Technique, highly esteemed anywhere under Heaven.

Yet, a Movement Technique that accelerated forwards after retreating was unheard of. At least, to Nogal, that is.

As such, this resulted in him attacking first, but finishing his move later.

Nogal shouted desperately.

"MY LADY, RUN AWA-"

"Nope. Where do you think you're going? That's a no-no. Stay put."

A-Qing threw a punch straight towards Nogal's mouth.

A fist that reached out in a gentle and sluggish, yet fluent curve.

It was the First Movement of the Circle Fist, Fierce Hole of Avarice, a common Fist Technique found rolling around everywhere in marketplaces.

Nogal deflected the punch with his upper arm.

But right as he did so, a left hand came in immediately after!

It was crookedly straightened, neither fully opened nor clenched. It was the unique grip technique of Praying Mantis Fist. The deployment of the Praying Mantis Hook was obvious; the Second Movement of Praying Mantis Fist, Orchid Strike. 

Then, it was followed by the Five Iron Feet Move of the Mandarin Ducks Kicking Technique, the Three Point Opening of Short Boxing, Reverse-Earth Chop of Liu Family's Fist Techniques\footnote{Fist of the North Star/Hokuto Renkitoza}, Wolf Strike of the Wolf Fang Fist\footnote{Dragon Ball Z}.

Every single one of them were common boxing and kicking techniques found in markets.

For such martial arts with a White Border, raising them to One Star required very few Free Practice Points.

They were no different from learning them for free.

That was why A-Qing had learned all the White Martial Arts from every bookstore she visited.

She didn't use the Sword Art of the Yue Maiden, considered cheat-like even among Purple Martial Arts, simply because she didn't need to.

Achieving One Star meant memorizing the very basic movements.

Even without knowing the movements true intention, spirit, operation of True Qi, or its applications, merely mimicking the external form properly was considered achieving One Star.

However, even a shallow imitation, when compressed with immense Qi and speed, could not help but to become a powerful martial art.

And what about, lets say, if dozens of martial arts were mixed haphazardly together?

That was the very spectacle A-Qing was currently creating.

Nogal was cornered.

"You bitch!"

Makgwi charged at A-Qing's flank.

Her left hand moved.

It was a flick, as if swatting a fly.

Suddenly, a resonant and profound sound of a bell echoed!

DWOONG-!

An invisible force traveled a distance of 2 chi \footnote{Chinese unit of length. In this novel's time, one chi is about 30.9 cm}(about 60 cm) and struck Makgwi's chest.

It was a Palm Technique for striking from afar, called Air Palm.

Makgwi flew like a cannonball and crashed into the back wall of the teahouse.

For a moment, A-Qing frowned and stopped her offensive movements.

Taking it as a kind of permission, Nogal hurriedly rushed to his junior.

"Makgwi! Snap out of it!"

"\textit{Cough}."

His chest was completely caved in. His thoracic cavity shattered.

Bone fragments had torn all his internal organs.

The bloody cough was essentially Makgwi's last words.

"Makgwi!"

Nogal cried out in anguish.

Not all those in the Unorthodox Faction were scheming backstabbers.

In fact, they were often bound as tightly as they were cruel to others.

A-Qing muttered, looking at the scene.

{\itshape Ugh, shit. I couldn't actually feel anything in my hand...So unsatisfying

Should've just learned something else.}

It was a harsh critique of the Buddhas Palm.

It made sense; A-Qing used a sword.

The sensation of slicing through muscle and bone, the feeling of her palm holding the sword, was near ecstasy to her. 

The hardships in this strange land with a different culture and common sense.

The number that always flickered above peoples heads.

The status window that rattled her mind every time she looked at it.

Compared to the exhilaration of her blood turning even hotter in a body already heated by battle, all of such things seemed utterly trivial.

Techniques involving fists and palms lacked that certain taste.

Striking and breaking things wasnt entirely devoid of satisfaction, but of course, it couldnt compare to the sword.

Above all, not seeing blood was her biggest point of discontent.

{\itshape In that sense, I can't use the Buddhas palm.

Sure, even a glimpse of its power as a mere One Star was formidable.

It was undoubtedly a powerful martial art, but-

It lacks that delicious sensation in my hand.

Do you even know how important it is to feel the impact when hitting? It's the most important thing ever!}

Suddenly, a thirst surged within her.

\textit{Blood. I need to see blood. I had to see it.}

"Hey, skip the melodrama. I'm not interested. Let's keep going."

Nogal suddenly snapped back to reality.

The grudge he held was one that wouldn't be satisfied, even if he tore her to pieces.

However, his opponent was a peerless Master who could effortlessly execute Air Palm.

Of course, A-Qing wasn't that much of a Master yet.

It was a misconception due to the game system's corrections, which was unknown to him.

Nevertheless, Nogal's mission was to protect the Lady.

"I apologize for not recognizing a Master. Please show us mercy."

"Mere fodder dares to talk back?"

"Please, please, I beg of you."

Nogal knelt down.

And A-Qing snorted.

"Why? Did you never expect this day to come? Did you think you could continue living off of sucking others blood, sweat, and tears? Did you think you'd live a long life surrounded by a bustling family and die in their embrace with a smile?"

"That-"

"According to what Mencius \footnote{Chinese Confucian philosopher} said, ah, was there a Mencius? There must be, right? Since it's ancient China. Anyway, he said human nature is good. That's why people misunderstand, you see. They think anyone, even the wicked, harbors an inner righteousness and can be reformed."

It was a gross misunderstanding.

Mencius doctrine of inherent goodness didn't mean that at all.

It was a proposition that also held true in reverse.

Human nature is good. Thus, anything inherently evil is not human.

Even if they were your superiors, civil servants, or the sovereign of a country, if they are not good to you, they are nothing more than beasts.

You cannot be ruled by beasts, so raise your bamboo spears.

That was what Mencius meant.

He was a great thinker who advocated the earliest form of democracy. (Confucius idea of governance was too lukewarm as it emphasized fidelity in governance and service)

Thanks to him, A-Qing was able to indulge in her hobby without a single hint of hesitation.

A-Qing took joy in slaying the piece of shit scum.

And as the trash disappeared, the world became a better place. Thus, everyone would benefit.

It was the realization of a world where no one needed to get hurt.
