\chapter{Friend (3)}

Sang Anjin, the Escort Leader of Kunpeng Escort Group, was astonished.

{\itshape What was up with that woman's sociability?

She became friends with the legitimate eldest son of the Peng Clan of Hebei?}

She seemed somewhat shabby at first glance, but this was an impressive acumen.

Moreover, she was a whopping Late-Stage Peak Realm Master!

The world under Heaven was vast and many eccentric individuals who did whatever they desired lived in it, so it was not strange that such a Master remained unknown.

However, Sang Anjin was an Escort Leader who was akin to a pillar of the Escort Group. 

If an Escort Leader merely acknowledged, 'Ah what an abundance of eccentric individuals we have in Zhongyuan!', and moved on, they would have no excuse if they were thrown out from their job immediately.

After all, there were many pillars and the Escort Group would not collapse just because one was missing.

Connections! This smelled like a connection to network with.

Indeed, a young Master was precious.

In fact, the young part was more important than the Master part.

Moreover, she was someone untitled, unknown, and from the wilderness.

In some ways, she could be considered even more valuable than the eldest son of the Peng Family.

The eldest son of the Peng Family already had an abundance of solid relationships.

Kunpeng Escort Group was big enough to span two castles.

But that didn't mean they were comparable to the Peng Clan, which was no different from royalty in Hebei.

No matter how well he treated Peng Daesan, all he could do was break even.

After all, it was only natural for the Peng Family to be treated well.

However, A-Qing was different.

Gaze upon how skinny and hungry she looks! How greedily she devours the food until her stomach looks like it would burst!

It truly reaffirmed the fact that she had lived without much.

"It seems you like the pork slices? Hey, come here!"

"Ah, you don't have to order more. It's okay-"

"How could you say something like that? Of course, you should eat more. Bring some more pork slices here! A lot of them!"

"No, you don't have to go to all this trouble..."

A-Qing trailed off, feeling half grateful and half embarrassed.

As someone from the Eastern Land of Courtesy, A-Qing felt somewhat burdened by Sang Anjin, who was older and took excessive care of her.

If it were an old man filled with Evil Karma, she could have shit on him with all sorts of curses.

But it was hard to go against the instinct of respecting the elderly, ingrained in her very genes, especially when dealing with a kind elder.

"Three plates, huh? You are quite shameless. But that's to be expected."

"What did you say, you punk? Why are you provoking me, huh?"

"Was it that tasty? You cleaned the plate twice."

"There's no loss eating when I can, you know?"

Peng Daesan sighed deeply.

It wasn't that she was shameless (although that was true), but rather her lack of common sense was the bigger problem.

Well, looking at her state, how much experience could she have had in being treated by someone?

"Leaving a plate empty is considered rude."

"What are you talking about?"

"It's rude to clean your plate so thoroughly, to the point youre practically licking on it. At the very least, you should have left a few pieces."

A-Qing didn't understand.

"Leave the food?"

"Yes."

"If I don't leave it, it's rude?"

"You didn't know?"

"Why leave behind precious food?"

Why eat? Why sleep? Why breathe? The violence in her words was practically at such a level, as if she found that very question to be utterly ridiculous.

Peng Daesan clicked his tongue. Tsk!

"Look. An empty plate at the table is a disgrace to a host."

"Just like how a scar on the back is a disgrace to a swordsman?"

"...? Where did that come from? It makes sense, though."

The only thing someone who was being served could empty was their cup of alcohol.

All other food should be left in small portions.

An empty plate was an act that undermined the dignity of the one who treated them to the food.

Whether one was poor or narrow-minded, it did not matter; in the end, it meant they couldn't properly treat their guests.

If a guest emptied the same plate twice?

'Your hospitality was not satisfactory today, so the only dish worth eating was this, hahaha.'

That was what the implication became.

A-Qings eyes widened.

"Escort Leader, I was unaware, so I made a bit of a mist-"

"Haha, it is fine!"

Sang Anjin already noticed A-Qings ignorance.

He said it was not rude if it was done unknowingly.

What was rude was to do it even when one knew it was disgracing their host.

"So I need to leave some food, whatever it may be? No matter what?"

"If it's a simple meal, it doesn't matter. But when you are being treated, it is better to leave the last two pieces."

"Ohhh. I didn't know that."

What in the world do you know then?

A-Qing was slowly going through the process of becoming civilized.

In truth, living in a different cultural sphere was inherently difficult because of this lack of common sense.

Anyway. It was a valuable realization for A-Qing.

Leave some food behind when youre being treated.

It was indeed a precious lesson for getting treated more in the future.

A step back to gain more in the long run.

Honestly, she had already been fed a lot anyway.

A-Qing had already established it as common sense that it was natural to be served if one was a Master.

Unbeknownst to her though, the expenses of Escort Leader Sang had already skyrocketed due to the dining costs.

Even Peng Daesan was unaware of this truth.

For him, being entertained was as natural as breathing. After all, he was the eldest son of the Peng Family.

The details of a mere escort convoys situation were of no concern to him.

Yet, Sang Anjin did not exactly suffer losses.

It wasn't just because of the uncertain future profits from investing in a budding female Master.

He was already compensating for that loss in the immediate escort convoys operations.

After all, bandits from the wilderness had appeared!  

"Stop right there!"

"Troublesome. This body. Master."

A-Qing, who had been lounging atop the leading carriage and basking in the warm spring sun, drew her sword.

As Sword Treads bloomed, the bandits, who had emerged imposingly, walked backward ever so naturally and disappeared.

It was a sight reminiscent of time being rewound.

The largest expense when it came to distribution in Zhongyuan was this toll.

A-Qing had always thought there were many, many bandits in Zhongyuan.

But now, she realized that was only the tip of the iceberg.

Lone swordsmen holstering swords were not attractive targets for the bandits.

It was incredibly dangerous to mess with them and even if they did, it wouldn't pay off.

What that meant was that not many bandits dared to trouble or even come close to A-Qing.

Even at that mere level, she thought, 'Is it because its ancient China? Why the hell are there bandits everywhere?.'

But after joining the escort convoy, she understood the truth.

Every single mountain had bandits.

Every single valley also had bandits.

Even the secluded forests, devoid of most humans, had bandits.

If Peng Daesan hadn't warned her that, unless bandits gave them a reason to, they shouldn't attack, A-Qing would have carved herself a bloody path, piling up Righteous Karma Practice Points.

A-Qing realized.

Traveling with a rich group was comfortable and she was well-fed, but slicing up bad guys was a bit tough to do.

She still needed to see blood at least once a week, though.

As expected, there was no perfect path laid out in the world.

When one gains something, they would inevitably have to give something up as well.

Nevertheless, since her body was comfortable and well-fed, A-Qing did not particularly miss seeing blood.

Having obtained her target, the Buddha's Palm, her desire for more Righteous Karma wasn't as strong. A thousand points seemed too grueling anyway.

Whilst A-Qing gradually became lazier, the Escort Groups carriage rolled all the way to Luoyang.    

-\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Even A-Qing knew that Luoyang was the name of a city. But all she thought about it was that it must be big.

After all, she had seen it in the Romance of the Three Kingdoms.

Except, even if it was such a famous novel, she had only read it once.

As such, she only knew about Guan Yu, Zhang Fei, and Zhuge Liang.

However, the actual Luoyang she saw was grand and majestic, even to her modern sensibilities. 

It was not for no reason that Luoyang was called Luoyang Castle.

Throughout its long history, Luoyang had been a fortress that had endured countless actual wars.

The walls, taller than those of modern commercial buildings, stretched endlessly on both sides.

The open gates were utter chaos, vomiting out and consuming an ultra-high-density population that was a mix of people and carriages.

Honestly, A-Qing had a tendency to look down on the civilization of Zhongyuan.

After all, her view was that they were roughly better than primitive men. 

As a modern Korean, it was an inevitable perception of ancient China.

The proud and magnificent aspects of ancient China had all been burnt to ashes by the collective will of those Red people, so modern Koreans had neither heard nor seen it.

Especially the height of these walls!

She thought she wouldnt ever be overwhelmed by height.

After all, she had lived in an era of skyscrapers like the Eyeball Tower of the Rings\footnote{Lotte World Tower} and the so-called Second Whatever\footnote{a building in the works that is called the Second Lotte World Tower} in Seoul.

Moreover, the density of the buildings was astonishing.

The walls that touched each other between neighboring buildings belonged to both.

The concept of an alleyway was non-existent, as the buildings were built continuously without a gap.

After unpacking at the Luoyang branch of the Kunpeng Escort Group and having a cup of tea with the Branch Manager, there was really nothing else to do.

"Hey, San."

"I do not want to."

"What the? I haven't even said anything yet."

"Weren't you going to say we should go explore Luoyang anyway?"

To her vexation, he was right.

But A-Qing had a reason she could not back down.

She didn't have money!

And opportunely, there was quite the reliable financier right here.

"If you follow obediently, there shall not be an incident of bloodshed."

Peng Daesan looked at her with a dumbfounded expression.

At times, such refined, high-class language would pop out from her, despite that formidable ignorance of hers.

How?

"My Moonlight Sword is starving. If you do not wish to become a sacrifice to the blood-red moon, guide me through Luoyang right now, Human."

"That's right. About that thing. I've been curious since before. The Moonlight Sword, you say? Isn't it just an ordinary iron sword?"

"Usually, it's only right to give your beloved weapon a name."

Peng Daesan frowned.

It was one of the most famous lessons for martial artists.

Do not name your weapon.

If a martial artist got attached to their weapon, they would hesitate and get cut down on the spot, according to the intuitive wisdom of Seniors.

However, having seen how A-Qing used that Moonlight Sword recklessly, he didn't really feel a need to explain that to her.

When she started poking the campfire with a sword (Moonlight Sword, No. 6), complaining about how she was bored, he doubted his eyes.

Using a sword as a poker transcended being frugal or reckless; it was an issue that warranted questioning the qualification of a swordsman.

"Fine, let's just say that's the case. Then, why is it called the Moonlight Sword?"

"Since I'm a Master of the Swords Arts of the Yue Maiden?"

"...?"

"Sword Art of the Yue Maiden. Moonlight Sword."

"...?"

"Do you not get it? Yue Maiden Sword. Yue (Moon). Girl Sword. Moonlight Sword."

"...Just stop talking."

The Yue Maiden was an abbreviation for a woman from the State of Yue.  

And of course, the State of Yue didn't literally mean the Moon.

After all, how could a states name be the Moon?

"Anyway, lets go. San. Luoyang is waiting for us."

"I said I'm not going."

"I'll pester you until you go. Just surrender obediently."

Peng Daesans eyebrows twitched.

The declaration lightly touched upon his sore point. 

At first, she seemed like a Master of the sword, rather than a woman. Then, she became more akin to an ignoramus. And then, a beggar-like presence. Now, she was something similar to a friend. But...

Her clinging onto him to such an extent raised suspicions about her motives.

Could it be...some kind of strategy? That she was actually a woman? For him to notice her?

It was an extreme case of erotomania.

Luckily, the nonsense A-Qing blurted out without thinking extinguished that spark of delusion caused by her words.

"We'll eat dinner at Diaochan Dining. Do you agree?"

"You...Do you even know what kind of place that is?"

"I heard it's the best in Luoyang, though? I overheard the escort members, you see."

It was true that it was Luoyang's best.

After all, Diaochan Dining was Luoyang's greatest brothel. 

"It is expensive there, though. And you don't have money, no?"

"What else would friends be for? When will I ever go to such a superb inn in my life? Isn't that right, San?"

It was a blatant maneuvering that implied she would leech off of him.

So, it was not seduction, but just plain freeloading.

Peng Daesans suspicions, practically at the level of a disease, subsided.

Instead, his mood subtly soured. 

Why did he feel so annoyed?

"Alright, fine, I'll be generous. Then, even if it's not at the level of Diaochan Dining, can w-"

"Fine."

"Eh? Wot?"

"I said fine. I'll take you. Diaochan Dining."

A-Qing blinked.

"Really? Didn't you say it's expensive? San, are you serious? Were you a man with that much wealth?"

"You told me to take y- No, what do you mean whether I have that much wealth? Are you seriously asking me that?"

"It was just a negotiation strategy, you know? Start with a big request, and if refused, make a smaller one."

It was a sharp wisdom that sometimes popped up amid her usual ignorance.

This time, it was particularly piercing.

Peng Daesan carefully pondered over her words.

Misunderstanding his silence, A-Qing sheepishly smiled in apology.

"If it's too much of a burden, forget it. I just threw it out there, you know? Just in case. "

Peng Daesans eyebrows twitched.

Her earlier comment about wealth. Could it be...

"Look. Do you even know what my clan is?"

"Peng Clan of Hebei, right? Escort Leader says it all the time."

"Do you not understand what that means?"

"You don't have to brag about your family being wealthy. Ohhhh. Sorry. Saying about how if it's too much of a burden or whatever wasn't a dig at your pride or anything, okay? Don't take it to heart."

She didn't know what kind of clan the Peng Clan of Hebei represented!

To her, it was just another wealthy household.

Even ignorance should have it's limits, shouldn't it?

A-Qing had probably only encountered sons of bitches or low-rate martial artists.

And they were those who couldn't even dare to mention the Five Noble Clans.

It made sense.

The Nine Sects One Union might forgive a bit of gossip behind their backs if one begged and groveled. 

But if one was caught badmouthing one of the Five Noble Clans, they would lose at least an arm.

At the very least.

"Diaochan Dining is not much of a burden. Let's go."

It was true that it wasnt much of a burden.

It was also true that his pride was a bit bruised.

But more than anything, Peng Daesans offer to accompany her was not just out of kindness. 

He had his reasons for not wanting to go out.    

And he was also curious about A-Qing's reaction to the brothel.

Right as the excited A-Qing rushed out the door, unaware of his thoughts-

She came face-to-face with an immense crowd of Luoyang beauties.