\chapter{Friend (2)}

Jade Qilin Peng Daesan. The Most Handsome Man Under the Heavens, Peng Daesan.

Peng Daesan detested his moniker.

He truly loathed it.

It was just a title stuck to him for being handsome, for having a good face.

Someone who received such a nickname and smiled about it was unworthy of being a martial artist. 

Peng Daesan was twenty-two years old.

At the mere age of twenty-two, he had reached the Mid-Stage Peak Realm. Truly a martial arts genius bestowed by the heavens, as well as one of the most outstanding achievements in this era.

But what? Jade Qilin? The Most Handsome Man Under the Heavens?

Could there be a greater insult than this in the world? 

Just look at that bastard called Shinjae from the Namgung Clan.

He had barely made it to the Early-Stage Peak Realm, but that bastard Namgung Shinjaes title was the Young Sword King.

It meant he was the next Sword King.

And Namgung Shinjae was even a year older than Peng Daesan!

{\itshape To think he's called the Young Sword King and I'm the Jade Qilin!}

So, Peng Daesan's personality became twisted.

But due to his fundamentally diligent nature, he didn't stray too far.

Instead, he completely forgot the concept of manners, especially towards women.

In truth, it wasn't entirely Peng Daesan's fault.

After all, he was the most eligible bachelor in the current era of Wulin.

Before all, he was handsome. Also, he had a good voice.

He was the eldest son of one of the Five Noble Clans in Zhongyuan.

Moreover, the Peng Family was famous for being the only one among the Five Noble Clans to not engage in political marriages.

Of course, it was also a family tradition that was being maintained because they enjoyed treating the other Noble Clans as petty, despicable, naive, idiotic misers who used marriages as transactions.

{\itshape For the Peng Family, such trivial, trifling matters were not needed in marriage except for true love!

But looks like that's not the case for you fools, huh?} was what they said.

Furthermore, Peng Daesan was an expert.

And he was going to become an even greater expert in the future.

After all, he possessed it all: looks, status, wealth, and skills.

As a result, Peng Daesan received the attention of all women within his vicinity at every waking moment and occasionally, even in his sleep.

And among them, the women who merely watched him were some of the better ones.

Everywhere Peng Daesan went, all sorts of things were left discarded on the ground. 

From embroidered cloth fragments to incense pouches, cotton-clothed daggers, and even repulsive sokgots

Thus, Peng Daesan never bowed his head.

He solely looked ahead and walked forward in a straight manner.

More aggressive women even attempted chest bumps, flinging their bodies onto him.

But it was a doomed endeavor from the very start to think that they could bump into a Peak Expert as if by accident.

It was a grossly inflated sense of self to think that if they fell, he would catch them before they hit the ground.

Peng Daesan was unsure whether to laugh or scoff at the women who flung themselves straight to the ground.

At any rate, Daesan had been experiencing extreme difficulties with women ever since he was young.

He was a female magnet that had reached its very extremity.

So, in front of women, Peng Daesan became increasingly impolite.

He lost all manners.

In essence, it meant that he wasn't interested, so they should get lost.

Honestly, A-Qings approach was not all that surprising to Peng Daesan.

He had experienced all sorts of bizarre incidents under the guise of differentiated dating strategies.

As such, he even had a general classification system.

If he was to classify A-Qings approach, it would be a mix of the Bold Woman and Funny Woman strategies.

Successful cases of the Funny Woman strategy were incredibly rare, so A-Qings move was somewhat commendable.

He laughed for the first time in a while.

He didn't expect Asura at all.

To think she would make such a sacrilegious joke.

And then came the Rough Woman strategy.

It was just that the level was a bit...The guttural contents of her words seemed to belong more to a wretch from the back alley.

But then he got hit in the mouth!

What in the heavens was this?

Was this some retarded love story like 'You're the first woman to have ever hit me'?

As a result, Peng Daesane genuinely got pissed.

His already low voice became even lower due to his wrath.

"I've dealt with all kinds of crazy bitches, but."

His voice carried a subtle killing intent.

Reacting to such a murderous aura, A-Qings Heavenly Slaughter opened it's eyes from its slumber.

A-Qing thought she saw blood as a way to relieve stress. And that stress relief was a way to protect her heart that was wounded by the matters of Wulin.

But in reality, once triggered, she became an actual crazy bitch, swayed by the killing intent of Heavenly Slaughtering.

It was a passive impulse to massacre.

Originally, if one was intoxicated by the killing intent of the Heavenly Slaughtering Star, one found pleasure in carnage and bloodshed. 

"Why you so pissed? 'Oive dalt wibb arr koinds wof cravy vitches, vut". But what? Does lowering your voice make you the shit or something? Hehe."

"Don't copy me."

"'Vont coby vee'. Then what? What you gonna do? Wanna hit me?"

At the very least, when it came to irritating teasing and obnoxious banter, no people of any ethnicity in this world could keep up with modern Koreans.

Peng Daesan trembled with rage.

The burning anger consumed him.

"I will not tolerate any more insults."

"'Oi virr vot torevate vany mov irvul', hey!"

Clang! The sound of a sword and a dao colliding sharply rang out.

"You struck first, okay? This is self-defense, okay? You really wanna try me, yeah? That's right, why should we blabber when we can use such nice swords?"

"I will not kill you. But I shall definitely cut off that flippant tongue of yours."

"You think you have the ability to do that? Go on, then. Try. Cut it. Nyehhhh-"

A-Qing stuck out her tongue.

Her unusually red tongue darted in and out mischievously.

"Nyehh-nyehh-nyehh-"

But the tongue stayed out a bit too long.

Seriously, she didn't know when to stop.

What kind of crazy bitch was this?

At this point, it was rather Peng Daesan that felt defeated.

Although he drew his sword in explosive anger, the sight of A-Qing making even more of a scene and causing chaos actually made him feel a sense of shame.

But he couldn't just lose to her like this.

His pride as a Mid-Stage Peak Realm would not allow it.

As such, he had to display just a hint of his realms strength

But right as he affirmed his resolve

Sword Qi surged in A-Qings sword.

The swaying, lazy white threads were vivid.

Sword Threads. It was a level of art and skill displayed by someone of the Late-Stage Peak Realm.

Peng Daesan scrutinized A-Qings face.

Her still shamefully darting tongue made Peng Daesan feel even more embarrassed.

But looking at A-Qings young face, barely out of girlhood, he had another thought.

If one broke through the wall beyond the Transcendent Realm, they reached the Creation Realm.

And such an echelon was also called the Unrestrained Realm.

When that happened, the body would regain its youth just once, practically traveling back in time. This was called Body Reconstruction.

A martial artist who had undergone such Body Reconstruction was, in fact, a monster of the human world, merely donning human skin.

A fight should be established among beings of the same kind.

Humans and monsters could not fight.

After all, it would not be called a fight but a one-sided violence.

"Uh, could I perhaps know which faction's Elder you are?"

"What the hell. You're stopping there? Geez, you're the type to stop mid-shit."

How could this possibly be the language and behavior of a woman?    

However, if he thought of her as a Supreme Master who achieved Body Reconstruction, it made everything somehow plausible. 

Come to think of it, didn't his Grandmother speak like that too?

And when hearing her, he had thought, women must have a rougher manner of speaking as they age. 

"I shall introduce myself again. I am Peng Daesan of the Peng Family."

"I'm A-Qing."

Suddenly, the tables had turned. The honorifics had reversed.

A-Qing smiled in satisfaction and thought to herself.    

\textit{This fucker got scared shitless, huh.}

Indeed, in Wulin, the strong were the law.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Peng Daesans misunderstanding did not last even a half hour.

It was because A-Qing oozed ignorance every time she opened her mouth.

Ignorance wasn't really the issue, but rather a lack of basic common sense.

For those who didn't understand her circumstances though, it was practically the same thing.

In fact, right now, Peng Daesan didn't even know why, what, or how he had misunderstood.

As such, the misunderstanding was easily resolved.

And then, Peng Daesan faced an entirely new crisis.

\textit{So this lunatic of a woman was a greater Master than me?}

"If it's not too impolite to ask, how old are you, Young Lady?"

"Me? I'm..."

A-Qing hesitated for a moment.

It was a bit much to say she was in her mid-thirties.

In the first place, even if she said so, no one would believe it.

After all, there had to at least be someone who pretended to accept it, for her to claim such an age.

But at the same time, it was also a bit much to treat someone who was no different from a mere baby as an elder. 

Baby.

From the viewpoint of A-Qings true self, a young man in his early twenties was still a baby who hadn't even been to the military.

This was all too universal and obvious for modern Koreans.

Besides, all he had to show was that he lived a bit well; he's weaker than me, you know?

"You first, Young Master Peng."

"I am twenty-two this year."

"I'm twenty-five."

"Truly? Is that correct?"

Peng Daesans skeptical gaze pieced into her.

"It's because I look young for my age."

"Really?"

"Mmm."

Lying also accumulated Evil Karma.

Insisting that her age was in the mid-thirties was somewhat true in a way. So, she should be able to push forward her agenda shamelessly.

Though no one would believe her anyway.

But what if she had to state the age of this body?

It wasn't worth accumulating Evil Karma over this.

As such, A-Qing answered honestly.

"Actually, I don't know either. I think I'm around seventeen, but I don't know whether I matured early or whether I'm really a twenty-five year old who looks young."

"How could you possibly not know your own a-..., I mean."

Peng Daesan was about to ask thoughtlessly but then waved his hand at a sudden thought.

A-Qing meant a child who wore blue clothing.

It was also the title of a peerless Master from the Spring and Autumn Period. The Yue Maiden.

Wasn't it said that the Yue Maiden only wore blue clothes?

According to historical texts, it was said that she had appeared out of nowhere in the crisis-stricken State of Yue and taught them the Sword Art of the Yue Maiden.

However, the Swords Arts was so mystical and complex that no one could properly master it. 

They only managed to create a sword manual based on the sword forms that were visible to the eye. But even that was a terrifying Divine Art. 

Armed with this Divine Art, the State of Yue attacked and destroyed the State of Wu.

In the end, the character A-Qing in the story was an idol among the female martial artists of Jianghu.

She was also an idol for women who dreamt of becoming a part of Jianghu.

And here was a woman who had taken such a clich name for herself.

On top of that, she didn't even know her own age.

If so...

Peng Daesan started to misunderstand arbitrarily all over again.

\textit{Could it be that she was a wandering woman with the background of an orphan?!}

But the misunderstanding that occurred this time was not as easy to resolve as before.

After all, one could not just ask someone if they didn't have a daddy and mommy.

It was possible that she was sincere when she talked about something as absurd as Asura.

A woman who grew up all in her lonesome might have had trouble answering questions about her lineage, founder, and ancestors.

A surname was not just the very first word of a name, but the pride of ones roots and kin.

Apparently, she grew up not knowing any of such things.

And that uneducated, vulgar behavior!

That ignorance that was akin to that of a moron!

"It is nothing. It was a slip of my tongue. I apologize."

"What in the world? Why do I suddenly feel offended? "

A-Qing cocked her head.

For some inexplicable reason, she felt like shit.

\textit{What's going on? Is another status window seizure coming? }

"Whatever. Forget it. Anyway, since we seem to be peers, lets just be friends."

"Peers, huh."

Peng Daesan had never heard someone of his age call him a peer.

Her choice of words was a bit...rRight?

Regardless of whatever he thought, A-Qing had her own calculations.

It was so obvious that he was a rich familys little darling boy.

Being friends with him seemed like a perfect way to freeload.

If she treated him like a little brother, she wouldn't be able to leech off of him.

But she couldn't call a baby Elder Brother either.

"Get it? Then were friends, okay? Understood, San?"

Peng Daesan was flustered.

Men and women should be distinct, yet she carelessly called him San?

"Uh, Young Lady? Even if were friends, how could you call me San?"

"If I say San! Then you have to say Qing! Just like that. San?"

"But still, for a man and a woman to be on such intimate terms wi -"

"Hey, why would there be things like men and women among friends?"

"Isn't that usually the opposite of what is said?"

When he asked as such, A-Qing replied confidently.

"Fine. Let's say that friends don't exist when it comes to relationships between men and women. Then, isn't overcoming that what true friendship is about?"

Mm?

That kind of made sense.

"You got it? San? San? San? San?"

She was a very insistent and noisy woman.

It was obvious that she intended to keep babbling until he responded.

As such, Peng Daesan reluctantly agreed.

"...Qing."

"Your voice is too soft! Again! San?"

"Qing."

"I can't hear you? San?"

"Qing."

"San?"

"QING! Qing! I get it, so please stop pestering! Please!"

Peng Daesan finally shouted out loud.

A-Qing grinned in satisfaction.