\chapter{Friend (6)}

Unwarranted rumors must not hinder a friends marriage prospects.

A-Qing took active measures to prevent potential problems.

"Ooooh, is that from personal experience? You seem to have a lot of experience with the opposite sex, huh?"

"Uh. It is something I heard from my uncle."

"It'd be fine to just laugh it off if things go as you say, but what if my friend here has someone else in mind?"

"Uh, uh?"

"Once words are spoken, they can't be taken back. So, rumors obviously spread. If that's the case, wouldn't my friend be unable to meet his destined partner then?"

"That-"

"What if my friend ends up growing old alone, regretfully reminiscing about the past, thinking, 'If only Senior Brother hadn't blabbered nonsense, I wouldn't be so lonely without a family, eating meals all by my lonesome'? How would you take responsibility then?"

"Oh no! I apologize!"

Hwangbo Uncheok was utterly demolished by A-Qings verbal attack.

"Little Brother! I apologize to you too! It is all my foolishness that almost led you to being old and lonely!"

Peng Daesan cocked his head.

"Why do I feel offended even though I'm receiving an apology? And it also feels like weve been in this situation before."

"Brother Peng, that is called dejavu. It is similar to when the upper dantian foresees brief moments of possibilities. It aligns with the Clairvoyance mentioned in Buddhist scriptures. By knowing the future and understanding past lives through Prvanivsnusmti, one transcends it through sravakaya and enters the gates of the Three Types of Suffering, thus freely manipulating-"

"I am going to lose my mind. Seriously."

Hearing a familiar topic, Zhuge Ihyeon joined the conversation, speaking at superhuman speeds. 

Yeah, that was just like him.

At that moment, A-Qing stood up abruptly.

"Where are you going?"

"Imma go take a dump."

Peng Daesan rubbed his forehead.

Was she actually a crazy bitch?

"Oh my, she is quite the outspoken Young Lady!"

"Can you really consider that as just being outspoken?"

"I am not quite sure!"

After A-Qing hopped away, Hwangbo Uncheok switched to a different topic.

"At any rate, this is a good thing! Little Brother Peng, you are on your way to Mount Hua, yes? Then we should move together from now on!"

"Are you also headed to Mount Hua, Brother Hwangbo?"

"Of course! Why else would I be here!"

The Hwangbo Clan, though not part of the Five Noble Clans, was still among the Ten Noble Clans of Zhongyuan.

This meant the opening of the Absolute Sword Wall was intended for the Ten Noble Clans, instead of the Five. 

For what reason would they seek the help of the Ten Noble Clans, though?

Perhaps something unusual was unfolding in Jianghu.

But putting aside that uncertainty, there was indeed something unusual happening behind the teahouse, at least..     

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

One thing A-Qing could not tolerate in the Wulin Zhongyuan was the outhouse.

However, A-Qing was powerless to do anything about it.

So what if it was intolerable?

It wasn't like she could fight with an outhouse.

But she would not endure it forever!

Once she became a fucking munchkin Master and held Wulin in her hands

She would follow the legacy of the late Shim Jae-deok, the former mayor of Suwon, founder of the Korea Toilet Associaiotion, and founder of the World Toilet Association, thus modernizing the outhouses of Zhongyuan.

Her ambition was grand, but it did not solve the immediate crisis.

A matter concerning a humans dignity, which was-

\textit{Please be clean. Please, please.}

After all, a dirty outhouse could kill a persons soul. Truly.

A-Qing firmly grabbed the outhouse door, strengthening her resolve.

That was when it happened.

You.

A-Qing turned around at the chilly voice.

A beauty who looked like a bitch was pointing a finger at her, flanked by two men with a nasty impression.

Clearly, she was a bitch backed by thugs.

However, one should not judge people by their appearance.

It was because perhaps they suffered because of their fierce looks despite being kind-hearted.

A-Qing checked their Karma instead of their physiognomy.

-498. The ones on the left and right were -621 and -455 respectively. 

Ah. So she was a piece of shit bitch.

Just as expected, physiognomy was a science!

The essence of statistics spanning over 2000 years!

In modern terms, it was 2000 years of big data! And today, in this place, it has been proven right!

A-Qing usually did not hold back in the face of evil.

Even if it was a beautiful woman.

But A-Q was also facing a major crisis.

It was a problem of whether the outhouse might be dirty, a matter of ones personal dignity.

Before opening the outhouse door, its condition existed in a state of both cleanliness and filth.

In essence, it was Schrodinger's Shit; a mixed state that became fixed to one reality based on the observer's observation. 

Humanity had always longed to overcome this chaos.

Believing that good deeds would bring fortune to them later was the result of that desperate effort.

In modern times, this methodology had evolved into reading cryptocurrency graphs; an attempt to fix the future overlapping states of rise and fall into a more electronic manner. Or they performed gacha rituals while listening to mythical music in front of the game developers photo.

Qing, too, followed such methodologies.

If being generous in her words could lead to a cleaner outhouse, A-Qing could even be kind to evil.

"If it's perhaps a small one, you can go in first."

"What is this thing saying?"

"A big one is a no-no, though. But if you're in a rush and you're confident you can finish quickly then-"

The beauty burst out in anger at the following bullshit that was spouted.

"Do you even know who I am to dare mess with me?"

For reference, people could also speak with their facial expressions.

And A-Qing's expression said all that it needed to. 'How would I know who you are? '

Instead of the lady, the man beside her on the right answered.

"This Lady is the esteemed daughter of the Black Shadow Association. She is one who someone like you should not even dare to make eye contact with."

A-Qing let the words go in one ear and out the other.

If one shouldn't make eye contact with her, then was she Medusa or a Gorgon or something?

Or was she the late Big Bro Jackson\footnote{Michael Jackson}?

A-Qing was confident she would faint just like a fan from that era if she met eyes with Big Bro Jackson.

"Ohhhhh, I see. So you're just too embarrassed to reveal your identity with your own mouth, right?"

"YOU!"

"My Lady, please calm down. There is no need for you to directly deal with that thing. If there is a commotion, Young Master will know, after all."

"Ahem, thats right. Nogal."

The Young Lady of the Black Shadow Association gestured with her chin, perfectly playing her role as a person of evil.

Nogal, the villain (previously on the right), tossed a pouch. The sound of money clinking was unmistakable.

It landed precisely at A-Qings feet, clearly not the work of someone who had thrown it like this just once or twice.

"Take that and cleanly stay away."

A-Qing swiftly picked it up and checked inside. Among the silver light, there was exactly one deep yellow thing.

A smile spread across A-Qings lips.

Oh my word, to think she would throw an entire moneybag just to ask her to yield the outhouse. Was this the grace of the rich?

But of course, it wasn't just about yielding.

It must have also included a fee for her silence regarding this.

A lady of high status using an outhouse would definitely be a little, no, very embarrassing.

Or maybe she was someone with severe constipation.

"Oh my, oh my, I apologize for not recognizing such a noble lady. I did not see anything. Please take care of yourself, my Lady."

A-Qing bowed deeply and retreated.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

This was what it truly meant to return in glory.

A-Qing straightened her grand chest, beamed a bright smile, and walked back triumphantly.

All three men averted their eyes.

After all, they knew where A-Qing was coming back from.

A-Qing interpreted the avoidance of their gazes differently.

Since it was a gathering of men, they must have been sharing some juicy stories.

A-Qing liked erotic conversation too. 

How could they discuss such important matters without her!

However, she knew that lewd topics were uncomfortable to share with those they were not familiar with.

Oh well, even if she was a bit sad from being left out, she just had to endure it.

Instead, A-Qing proudly showed off the moneybag.

She even opened it up to show what was inside.

When Peng Daesan peeked inside, he saw it wasn't much.

For an heir of one of the Five Noble Clans, it wasn't even one day allowance.

Seeing her being so proud of such a small sum was a bit adora-

Suddenly, a chill ran down Peng Daesans spine.    

What was that just now?

While Peng Daesan was facing some cosmic horror, A-Qing stated proudly.

"Look at this. I just earned some money."

"Wait, Elder Sister."

"Elder Sister?"

"If you are Brother Peng's friend, wouldn't that make you an Elder Sister to me?"

The title Elder Sister felt strangely unfamiliar.

But it definitely seemed better than being called a Young Lady.

"Ooooh. Then I'm gonna speak comfortably, okay?"

"Of course. How is it that you managed to earn such an amount in the lavatory?"

"Because someone just gave it to me? They were in such a hurry to use the outhouse, so they asked me to yield it to them. I mean, they said they would give money for it, so how could I possibly refuse? I'll go back there later."

"Oh my, oh my. How desperate were they to do such a thing."

Zhuge Ihyeon trailed off.

Even to him, a precious child of the Jegal Clan, it was a meager amount, barely enough for one day allowance.

But still, it was a lot for just one use of the lavatory. 

Oh well, income and an understanding of the economy were different things, after all.

Right then, the little Hwangbo Uncheok joined the conversation.

"Young Lady, taking advantage of someones desperate circumstances for your gain is not right."

"But it was a noble lady from a very wealthy family, wasn't it? The one who has desperate circumstances is me. This very body. I don't have money, so I'm purely relying on my friends kindness to eat and live."

"Regardless of their wealth, taking unfair advantage is still not right, is it not?"

"Pffff, how can we possibly separate wealth from this matter? Well then, Little Supreme Justice? Why don't I pose a question for you? What if, hypothetically, you were about to shit your pants? How would it feel then?"

"Well, that-"

"What if, Little Supreme Justice? How would the world see you after you shit in your pants? Of course, they wouldn't say anything to your face, wouldn't they laugh behind your backs? Regardless of whether it is about the Little Supreme Justice? Even other righteous people could be targeted as well because of you, you know?"

"Uh, that-"

"Social status is one thing, but shitting your pants is a serious, irreversible damage. A stain that might never be erased in a lifetime, don't you think?"

"That does seem to be the c-"

"I see it as a social death sentence. Haven't you heard the saying that a person doesn't die when their life ends but when their name is forgotten? Wouldn't being remembered as Pooper or Shitter be a humiliating, disgraceful fate worse than death?"

"That is obviously t-"

"So, in essence, I protected something more precious than life for that person. The value of their life. And the token of gratitude for that, from them to me, is just one gold piece? If that's the case, couldn't it mean I'm the one who has been slighted instead?"

"One gold piece certainly seems a b-"

"But in a moment of life-threatening urgency, mistakes can happen. And since they gave the entire moneybag, they must have given all they had, right? So, it wouldn't be right for me to complain like 'How dare they only give this meager amount', would it?"

A-Qing fired off her words rapidly.

And Hwangbo Uncheok responded with a serious expression.

"Truly! Your generosity is as vast as the sea, Young Lady! I have made a great mistake once again!"

Zhuge Ihyeon, sitting next to him, also expressed his admiration.    

"Remarkable! Elder Sister! You elevate bullshit to the level of obvious principle so naturally with your leaps in logic! And yet, you raise your own status so naturally at the same time through this bizarre narrative! It is utterly unpredictable and endlessly changing! It was a marvelous debate that has reached the realm of Flowered Tree Grafting!"

A-Qing was renowned for her ability to read others, even before her military service.

She was adept at probing and poking just enough to gauge where the line was and whether she could tease them, truly standing at the very pinnacle of these studies.

She was a giant among men. Even though she was a mere private, she was able to casually joke and laugh with Corporal Kim, the disciplinarian of their squad who was known for his temper and son of a bitch personality.

And now, that very same giant stood tall in the room.

"Elder Sister? Why are you standing sudde-"

"What do you mean why? Obviously, I have unfinished business to attend to."

"Ah."

Zhuge Ihyeons face turned bright red.

A-Qing then left through the back door of the tea house.

The timing couldn't have been more perfect as she bumped into the very person she was grateful to.

But the woman pointed a finger, her entire body trembling.