\chapter{A Loner's Journey To Solitary Sword (4)}

She just sat there, looking like a beggar and smiling like an idiot.

It was a fact without any exaggeration.

Did you do a beggar thing? Yes.

Are you smiling like a raccoon? If you look closely, yes.

Are you sitting? Yes.

No, don't the people who see it think about it?

It was a free spirit that was not bound by the past.

"Oh, I can't live like this. Why were you doing this? Is it because you don't have money?"

"No. I have a lot of money. I'm rich."

Xue Iri opened her pouch and showed off its content.

Although it was not completely yellow, there were quite a few gold hues here and there.

For some reason, everyone looked down at Xue-i-ri with a sad look in their eyes.

Sure, it was sufficient amount for a commoner, but why she claimed she was rich?

Even though Qing didn't know it, isn't she the true wealthy man of the time who owned all the property (including people) of the Heavenly Demon Cult?

What about the rest of the members of the Half-Sword Double-Saber Association?

They were filthy rich.

Weren't these the children of the Ten Great Families of Zhongyuan who, when asked for allowance for going out, would receive a whole gold nugget flying around, so they had to specifically ask for silver coins because it was a hassle to give change?

Even the wealthiest of them all, the Tang family's Tang Lan-ah, did not even need to carry money when in Sichuan.

You. Don't know. Me? Just three phrases were all she needed.

Later, when the Tang Clan was charged with bills, they'd pay double, so everyone was waiting with bated breath for the young lady to come.

"No, you have a lot of money, so why were you homeless?"

"I heard that Lady Ximen was staying here."

"Then you should tell them that you're my friend that came visiting."

Xue-i-ri shook her head.

"No. Everyone knows where Lady Ximen stays. Don't show off. There were many people with bad intentions."

If you act like you know someone and act like you know them, there will be people who try to do it for reasons such as friendship or affection, even if they were not enemies.

So, what she was saying was that she was being considerate of Qing and just kept waiting until she came out.

Well, that's strange.

If you say so, what kind of example would that be?

"Ah. Ahh……!"

As expected, Gong Sun-Yaoyi lowered her head with a sigh.

"I guess I'm not even worthy of being a friend…."

"Young Lady Gongsun? That's fine. Yi was a normal person, isn't she? Who on earth would slept out in front of the inn like that?"

"But Young Lady Xue-"

"Originally, Iri sleeps well outside, right?"

"No. No."

"Is this a lie or not?"

"No, yes."

Xue-i-ri was shameless and her complexion didn't change at all.

When she had followed me, she said she had no money, so she tried to sleep in a ditch dug in the rainy season, or to be exact, she ended up getting flooded while I was sleeping. What was this?

And if you see a person, don't you get up a little?

Why are you still sitting on the floor with some kind of glue stuck on your butt?

"You're not going to get up?"

Then Xue-i-ri raised both hands high.

Oh my, there were so many different things.

Just as Qing was about to lift her up, something small rushed over and grabbed Xue-i's hand.

"What, you don't have hands, you don't have feet?"

"No. No."

"Why does she talk like that? Was she always like this?"

"Hmm. I just realized she can speak. I thought she didn't know Zhongyuan dialect."

This was an addition to Peng Daesan Mountain.

And then, a struggle ensues between Tang Lan-Ah, who tries hard to pull, and Xue-i-ri, who tries hard to hold on for some unknown reason.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Life and death were ruined.

Even I wouldn't want to rush in here, so yeah, Inpimyeon-gu, if there's even an Inpimyeon-gu, then that's fine.

It was Qing who realized once again the power of the Inpimyeongu.

Those were the good times, when all I had to do was wear a piece of cotton and there was nothing to fear in the world… … .

I never thought I would end up like this, so isn't that a sign of a total thief?

Shinto had chosen one of his next Shinto moves very well.

In fact, at this point, I think the crowd was tired of watching the life-or-death situation.

When Heavenly Blossom Sword was alone, he cackles and shouts rude things like Samdugain and Odubangjeong, and even the daughter of Gongsun Gongga was sitting there.

Although the Gongsun Gong family was a new and hot family that has been included in the Ten Great Families, a nearby wolf was scarier than a distant tiger.

For the people of Jiangsu Province, wasn't the defeat of the Donghyang Dynasty more frightening than the Five Dynasties before that?

Despite this, the number of spectators in the arena did not decrease, but rather increased compared to before.

There was no need to say anything about who the culprit was.

Since Ok Gi-rin has appeared, it was only natural that a group of extremely passionate women will be dispatched.

No, where on earth do these guys come from?

When the jade giraffe appears, where does it naturally appear?

Despite the many bad reviews about Peng Daesan Mountain, there were ardent followers who steadfastly declare that they will never lose our Okgirin brother and will absolutely protect Okgirin.

Some of them were wearing beggar clothes that have been torn off, but only their heads and faces were neat, giving them a strange appearance of strength.

And the majority of the intersection is-

"Wow, look over there. That's awesome. If you're going to do that, wouldn't it be better to just not wear a top?"

As part of his efforts to eradicate his followers, Qing advised him to focus on the women among them who had the most exposed breasts.

If you can bear the reputation of being lecherous and frivolous, wouldn't some of you still fall away?

Since Peng Daesan did not care about reputation, he found Qing's advice plausible.

The result was a feast for the eyes of the Qing.

But when I first gave the advice, didn't I reveal that I had a selfish interest in wanting to see it, so everyone would be open about it?

So, Qing was confident.

"Sansan, over there, over there, that woman with her bottom exposed, wow, I can see her nipple. Isn't it windy?"

"……Do you really need to say that out loud?"

"That? That thing? What was that?"

Qing pokes Peng Daesan's ribs with a sinister smile.

"No, that, haa. There's nothing you can't do."

"Hmm. That's it. I don't know. Oh, can you explain, Zhuge? What was it?"

This time, Zhuge Lixian was being stabbed.

Zhuge Lixian bows his head deeply with a flushed face.

Huh. What kind of kid was that big, distracting guy?

A teenage boy? Without a clue.

Isn't that right? Zhuge was the youngest, right?

Come to think of it, isn't Zhuge a boy in puberty? He's in late puberty.

The female members have complex expressions.

Among them, there was one woman who was particularly gloomy and shadowy.

At that time, Nan-Gong Shencai calls for Qing.

"Oh. Sword Friend. Look at that woman over there."

"Huh? Where?"

"Beside that bright red soldier, why was that woman with her breasts clearly visible through the light green cotton?"

"Uh, that person? Why that person? There's nothing special about him."

It was a sound that would make anyone who heard it cry.

"No, not his chest. Look at his arm length. It would be perfect for wielding a sword. It'd extend a hand's length for his height."

I was just watching him without saying anything, so I thought maybe he was just a man, having a nice complexion, even though he was always talking about swordsmanship and training.

"My body feels achy even though I'm still sitting still. Would you like to have a round of sparring?"

"In front of so many people?"

I don't mean to be embarrassed.

The more secretive a martial art is, the more difficult it was to deal with it, which was why martial artists do not show off their swordsmanship in front of others.

"Hmm. Just use what everyone else knows. So, you know the Ihwa Sword? If you don't, try learning it now. It's quite deep for a swordsmanship so common in the author's world."

"Huh? I know that."

"As expected! I knew you'd know, Sword Wu. Surprisingly, the more widely known the swordsmanship, the more honest and simple it is, embodying the fundamentals of swordsmanship. Would you like to learn a few while you're at it? Do you know the Dancheolgeom?"

"huh."

"What about the Ilhwa Sword?"

"I know."

"Eunsal sword, chamwoo sword, jade sword type, long-sword style."

"I know everything."

"Excellent! As expected of Geomwoo! Well, I apologize. I seem to have underestimated Geomwoo's passion for the sword. As for my Geomwoo, he must have been exposed to and practiced swordsmanship."

It was just common.

If it were a common martial art, it would be easy prey for the Qing, a martial arts collector, a secret plunderer of martial arts book stalls, a terrible nightmare, and the master of brain-scratching sorcery at the tip of one's fingers.

"Yes, good! Everyone, why don't you all learn swordsmanship while you're at it? How long were you going to keep using half-swords, Peng? Now's the time to enter the world of swordsmanship. The same goes for you, Lady Tang. No matter how skilled you were in poison and secret techniques, a warrior must ultimately wield a sword."

The crackling sound of tendons was a double glazing.

In fact, in the Half Swordsmanship Club, it was rare to find someone who was not a swordsman.

The Peng siblings plus Nan-a, all of them.

But in the past, people would say that twin swordsmanship was not swordsmanship but a discipleship, but now Nan-Gong Shencai was the one who can just say that he has two swords.

"Saying it's a common weapon was like saying it's easy to obtain. How convenient would it be for a warrior to know even one sword technique? It's also convenient to pick up and use in battle."

"If what Nan-gong said was true, shouldn't we learn Taoism? Most of the Sapa people use Taoism."

"That's right! As Peng Au said, isn't that a weapon only the half-black Sapa use?"

Ppachik. Uncle, add one more tendon here.

Peng Daesan immediately regretted it.

Even though it was obvious that there was no way to have a conversation with Geomchi.

"Well, that's not a bad story, was it? If San-i learns a few swordsmanship moves, it'll be a huge help when fighting swordsmen. Lan-ah, you're already a poisonous brat, so it'll be difficult if someone tries to attack you."

"Huh? Me? I'm just going to take the antidote and detonate the poison bomb? There were a lot of explosive barrels."

"Well, that's only true when I'm alone."

"Hmm."

"And then you can learn half-swordsmanship. As San said, the Sapa guys use half-swords, so if you learn the Tao, you'll be good at dealing with half-swordsmen."

"That's a valid point, but I'll decline. Pure iron was not mixed with impurities."

No matter how ignorant he is, he knows that iron becomes much stronger when it was mixed with impurities.

But there was no need to respond to that nonsense, so Qing just pretended not to hear.

"Do I really have to make a half-sword sound?"

"Then let's call Sanido Ssangdo."

"……ha."

So instead of a life-or-death struggle, the event schedule was changed to a third-rate martial arts training session for the later indexes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Sister! Would you like to try this!? It's red bean pork. When it comes to Hoeyang cuisine, you can't leave out red bean pork."

"It's a raw dumpling. The bottom was fried in oil and the top was naturally steamed, um, it's a dumpling."

"Hey, Qing'er, would you like to try some of this? It's dark, and it's really hard to find a place that makes this well. Here, ah."

"My lady, this was lion head. It's a dish I really like, so if you try it…"

"Ximen Sojourner. It's high-pressure. They say that if you come to Jiangsu Province and don't try high-pressure, you haven't come at all. I dare recommend it, as it's the best among the Namnyeongchae."

The dishes flying towards me were empty, and even three chopsticks were outstretched.

Two of them were connected to Tang Lan-ah's hand, which was holding a large piece of fish head, and one was caught in Murong Ju-hee's fist, holding a large piece of meat.

What the heck? What the heck?

Do I look that hungry?

Qing looked at Wang Ssangryong, who was holding a small bowl of snacks carefully, his eyes fixed straight on hers, from a distance behind her.

And why, General?

"Um. Thanks, I appreciate it, but I have my hands—"

"Oh my, my arm was falling off. Qing'er?"

First, let's solve the problem of the fish's soft head shaking the baby's chopsticks.

Suddenly, a head pops up and snatches the flesh of the fish head that Qing had cut off as his share.

"Hey! What were you!?"

"Snowdrop. Snowdrop."

"This is, really……!"

The child's eyes sharply rise up like axe blades.

He did not miss the Qing's superhuman vision and Tang Nan's uncanny dexterity.

Of course, it was not only because of his eyesight, but also because he possesses the best golden technique of the Muyeongshinsu, and has the ability to recognize the golden technique of his opponent.

"Shh, Lan-ah. It can't be used. You shouldn't use poison."

"But, this kid."

"We have to get along. It's no use if we keep going like this."

"yes."

The answer was straightforward, though.

Why were these two always having a cold wind blowing?

Lan-ah, everyone has a bad habit of barking loudly, but Xue-i-ri also secretly keeps going against the grain.

Hmm. These two really don't get along…

The lion head that Lady Qingyi Moyong gave me? Holding the strangely named meatball in her left hand.

Then there were three plates in front of me.

Qing thinks about it and soon comes to a conclusion.

It looks like they're having a bet to see who can eat the most.

Then I can't lose either.

So I started eating like crazy.

By the way, what the general had was a snack and dessert from the land of Nanning called Jeokduwonso.

A sweet dessert made with sweet red bean porridge, made very finely with honey, and topped with honey rice cakes.

Hmm. It was delicious. I liked it.
