\chapter{A Loner's Journey To Solitary Sword (9)}

This primitive ancient martial arts world was a world of savage and vicious scoundrels.

It's different from Qing's hometown.

Resentment never ends up as a burning firewood, leaving ashes in the heart.

A world where you can prove it by cutting it with a knife so that there were no aftereffects.

What do you mean by the people of Zhongyuan to the Qing? They were a bit extreme, what should I say?

Are you good at controlling bipolar sociality?

To those close to them and to the strong, they were kinder than any other people in the world, but to those they don't know and were weak, there were no other dogs who were so cruel and ruthless.

Wulin of AQing and Ximen Qing were different in their colors.

If you think about it, before entering the Divine Maiden Sect, the world was nothing more or less than a gloomy, dark, and murky den of evil.

I don't know what it was about a high-ranking female disciple in the Jeongpa martial arts world that makes life so dramatically easier.

But this was because the blue was strong.

Even at the peak, I had no rivals of my age, and when I reached the peak of my power, the ultimate power, then no one but real monsters could stop me.

But what about my friends?

If I could, I would like to instill in their brains something like an incomprehensible cosmic force into the shape of the screen.

That's also impossible.

In the first place, just because they learn martial arts doesn't mean they become as strong as me, have sharp eyes and ears, or have superhuman abilities.

So I have to protect it.

I can step forward and clear out the dangerous stuff, and if there's a suitable bad guy, I can train him under my supervision and let him experience real combat.

So, you need strength.

It shouldn't be limited to being strong for one's age and having a promising future.

Power, power beyond the peak, power of thought.

That was why he sets foot into the valley of temptation, a place where no one, desperate for power, should enter.

The source of a person's consciousness, which was not clearly defined, as it was called by various names such as the spirit, soul, mind, or image of a person.

Snap.

Ripples form in the shallow pool of blood, and countless concentric circles spread out in geometric patterns.

On the other side was a huge wall made of sticky human byproducts, flesh, bones, ligaments, etc.

There was a small hole in the middle that tempts you to come in.

A hole leading straight to the mouth, at every mouth.

If you just cross that door, if you just crawl on your knees under your evil instincts, you can go beyond the climax and enter the next realm, the realm of the devil.

The original purpose of martial arts was to kill the enemy, and the weapon becomes obsessed with the impulse to kill the enemy.

But were humans creatures that cannot control their instincts and act as they please?

It's a grandiose statement, but in reality, it's not that difficult to suppress the instinct to kill.

Because people have more important things to protect than just impulses, such as values, relationships, social status, face, and property.

So, unless you're completely pissed off and your eyes were spinning, it's true that there's no way to tell the difference between a master of fire and a master of the mouth.

So just close your eyes.

Don't try to go against human nature.

If you crawl over the blood just once and soak your whole body in blood, a dreamlike realm was right there.

So, now that strength was desperately needed, it wouldn't be all that strange for Qing to step foot on the threshold of this palace… …but.

A thud.

He lay down on the ground, covered with a large towel, on the flowing blood.

The sight of her flapping her arms and legs reminded me of the challenge of drawing angels in the snow, which was briefly popular in her hometown in the past.

To most people, the scent of blood was a fishy and unpleasant smell.

But what about Qing?

Hmm, it smells good. Hmm. I want to eat blood sausage, blood sausage soup, blood sausage hangover soup. I can see blood sausage, dried radish greens, and bean sprouts piled high in a clay pot, and a mountain of soft, ripe, sour dried persimmons.

"Wow, my mouth was watering."

Qing lies on the floor with her arms and legs spread out, looking up at the evil stars filling the sky.

I don't know if that's real or not.

In the first place, this was the world inside me, similar to the one I'd been in before, where I'd been arguing with the mental parasite.

Just as I couldn't tell if the Mucheon Daeje I saw in the illusion of the cliff was the real Mucheon Daeje or if the MuQing Daeje was from me as he claimed.

There was no way to know whether that evil spirit was real or fake.

But what if it's real and what's fake?

Whether it was the Great Emperor Mucheon or the Great Emperor MuQing, he passed on the recipe.

What does it matter if it's a real thousand-year-old ghost or if it's a ghost that originated from me?

What matters was whether it helps or not.

And now was the time when that help was needed.

If it helps, why not ask even the neighborhood stray mongrel, not the Cheon Sal Go Seong?

Why did Confucius do that too?

"It's early, I've been trying everything to get a real Hwagyeong, but why isn't it working? Now, whenever I use martial arts, I keep seeing hallucinations. I don't know if they're real or just illusions, but the person who created the martial arts keeps showing up and giving me advice, saying things like, "This was it." Doesn't that mean I'm on the verge of Hwagyeong?"

[… … .]

"No, it's right in front of me, just a grain of sand, just this much, just a sheet of paper. I'm dying of frustration, but I can't find a way to express it. It's literally flashing before my eyes, but why can't I see it? Why can't I become a landscape? It's so frustrating, I'm going crazy."

[… … .]

"Excuse me? You can speak, right? Was that some kind of input recording? Mr. Cheon Sal-seong? Or Mr. Cheon Sal-go-seong? Any advice?"

[… … do you want power?]

It seems like he was responding reluctantly.

"Don't tell me to go in there. I've got all the copper I need, so why would I leave my mirror behind and go in there? Uh, just a little, can you tell me something that might be of some help?"

The dark night sky was almost completely filled with evil stars, and the countless eyes that stood out on its surface all closed their eyes in a sad manner.

If I had to interpret it as a nonverbal expression, it would be something like, "What kind of woman was this?"

Qing grumbled to him.

"Miss. Don't just shut your mouth like a mute and pretend you don't know. And what kind of trend was "wanting power"? Don't say things like that. I accepted it because I was the one. Where were you, the old-fashioned one, with your voice low and your flaws muffled? No, who would buy something suspicious? Wow, power! Yes, then just one. Oh, do you get it packaged? If I buy two, do you get a free power? I heard that at the twelve o'clock general store, if you buy two, you get one free. I wonder if it'll be like that?"

The surface of the star seemed to be wriggling somehow.

And then-

"Ah!"

Qing screams, clutching her eyes.

What shapes, what messy shapes that were seen with the eyes and penetrate the brain, dozens, hundreds, thousands, tens of thousands, and billions of shapes and sounds rush in at once to create an incomprehensible shape.

People, naked people, people stripped of their skin, beasts of bone, twisted limbs, obscenely entangling snakes, corpses, rotten corpses, mushrooms blooming rapidly on rotting corpses, flowers, flesh and blood, a burning universe, the unused shoes of the savage, spores blooming on living sacrifices, eyes, red eyes, blue eyes, irises split in two, into four, into eight, thousands of pupils contained in three eyes… …

"Ugh!"

Qing vomits out his stagnant breath roughly.

Before he knew it, the son-in-law was in a dim, swaying light source, and the decorations on the top-of-the-line bed were swaying.

And my chest was hot, but my left side was cold.

Where was this place?

Soju Jeilgaekjan Changtaeho Bigak Taeyong Wangsil.

Oh, I arrived in Soju yesterday.

I don't know why the Pojeongsa Temple was in Suzhou and not Nanjing, the city of the saints, but it would be impossible to refuse hospitality from the highest official of Jiangsu Province.

I went there with my friends, and surprisingly, the old man from Pojeongsa Temple was having a good time.

That long-term bragging was, wow, really great.

Such skill without even learning martial arts.

Qing recalls a fun drinking party.

And then, squirt squirt. What's on your chest?

Qing looks to the right.

The awkward and cowardly smile of Dang Lan-ah, who was in charge of poison in the five martial arts world.

"Oh. He. Awake?"

"……Aren't you sleeping?"

"I woke up too, didn't I? But I couldn't sleep. So just a little bit."

The little girl said this and bit into it.

"When a normal person wakes up, doesn't he just put his hands away or something? What was this confident attitude?"

"I was going to do that, but my hands keep moving on their own. What should I do? It's not intentional. Hey, what's wrong? My hands won't move."

"ha."

Qing took a deep breath.

No, was this guy possessed by a ghost who died because he couldn't touch his chest?

Yours isn't small either, so why was mine-

No.

When I think about it, my own was just a useless weight.

"My chest feels good. Yes. My chest. Touch it, touch it."

"Huh? Really?"

"I won't let you touch me, so you stay up all night, waiting for me to get a good night's sleep, and then secretly touch me. This was just plain lecherous. Haa, that's enough. You should consider it a blessing to be born a woman. Just touch me openly."

Come to think of it, aren't humans originally creatures that become more passionate and want to do something when they were prevented from doing so?

After learning the yo-yo trick from Heemae, I no longer feel the ticklish sensation that makes me lose my senses like before.

"Really? Then you just touch me?"

"uh."

"Are you just going to sleep?"

"uh."

"There was no softness?"

"uh."

Qing answered roughly.

I thought I'd say it when I got tired of it.

Suddenly, a sharp pain struck my head.

As Qing tries to brush her bangs back, she turns her head at the feeling of a heavy weight pressing down on her arm.

On the other side, sleeping soundly with his arms wrapped around me, um, dazzling.

Qing looks up at the ceiling again.

It was a truly harmful face to look at up close.

After all, it seems like tastes can't be helped.

It's so cold, it's chilly.

How does he sleep and use Hansimgong?

Of course, for the North Sea people, the issue was not about ice but about heating, which was a matter of survival.

Because all the North Sea people who don't know how to use Hansimgong unconsciously while sleeping have been wiped out, only those who know how to do it remain.

The sound of snoring softly.

As I've already experienced, Gunyeong was the type of person who doesn't wake up even if an elephant steps on him when he falls asleep.

Only after waking up from sleep will he scream in pain from being stepped on, and only then will Gunyeong grit his teeth and whine.

Well, that was quite a sight.

If you just press down a little bit somewhere- ugh.

A sharp, stabbing headache made Qing's eyes twitch.

I still felt as if those wild images were etched on my retina, behind my eyelids.

Could this be, really, the ultimate weapon used by the hometown telegraph warriors, a weapon for mental destruction?

This evil spirit who has turned around dares to approach me?

Qing closes her eyes.

And then splash.

"No, since your personality was like that, you're not a Cheon-sal-seong, but a Cheon-sal-go-seong, a loner with no friends. If you don't like it, you can just say no, if you like it, you can just say yes. Why do you keep forcing suspicion into people's heads like that?"

[… … .]

If the Thousand Year Old Castle was real, it would be incredibly absurd.

I've already said enough times that I don't like it, so what's a bitch supposed to say?

"You want something from me, don't you? If you're going to get something done, isn't it better for you if I'm stronger? So I'm asking for your help, but why were you keeping your mouth shut? I know you're talking. You know you'd laugh so loudly it would tear the planet apart…"

Qing trails off.

Oh, why do I know? Have I seen it before?

And then roll your head.

No matter how hard I try to remember, I don't think I've ever seen you smile like that. Why do I know?

Then suddenly-

Blood, tears, old men being trampled, a procession of the old dead, old women, very old women, grandfathers, half-dead grandfathers, old men being buried alive, blood and tears were gathered and flooding the world, so perhaps it was because in this advanced civilized society there was no country for the elderly… …

"What the heck!"

Qing suddenly jumps up from the bed.

Then, the embarrassed Tang Lan-ah quickly makes an excuse.

"Oh, that, I told you to touch it. Did Qing'er say it was okay to touch it? I might have been sleeping, but…"

"No, that's not it. It's because the dream was so bad."

On the other side, Xue-i-ri, who was thrown out while hugging her forearm, was curled up and snoring.

Qingi hissed.

Is this kid trying to do this with me right now?
