\chapter{A Loner's Journey To Solitary Sword (10)}

When you thought of Shuzou, the Taihu Lake comes to mind.

The name of the lake uses the character for "big" (太), so just hearing it makes you think it must be a really big lake.

And it's actually big.

The immense majesty of the lake, which stretches 170 li from north to south and 130 li from east to west, was so great that even though it was a lake, the other side cannot be seen, revealing the horizon.

If you convert it to the Korean unit of measurement, the hometown of the Qing, you can immediately get a sense of how large this lake is. It was roughly the size of four Seouls, or less than four Seouls.

This was where the Soju people's complaints lie.

In addition to Lake Taihu, Suzhou has many beautiful lakes, making it a truly beautiful city surrounded by lakes of all sizes.

Thus, in the north was Joho Lake, in the northeast was the large lake Yangjing Lake, in the east was Jingye Lake and Dokseok Lake, in the south was Yisan Lake and about 100 lakes, and in the remaining directions was Taihu Lake.

It was truly a city of lakes, with even the smallest lake exceeding the unit of measurement commonly used in the Qing Dynasty's homeland, one Yeouido!

But as far as being famous, only Taeho was famous.

Anyway, when it comes to soju, it was a city where the literary culture of Jiangnan and the lecherous people of Zhongyuan gather.

To put it nicely, they were lecherous, and the people of Zhongyuan think of them as womanizers, and their official name was literati.

And a beautiful woman appeared in Suzhou, the city of writers.

The Cheonhwa Sword, said to be the most powerful candidate for the most beautiful sword in the world, was definitely the Shinryong Sword, said to be the most beautiful sword in the world, even though its appearance was unknown.

To be precise, Qing was quite different from the beauty pursued by the literati of this era.

A beautiful woman should not only have a beautiful face but also a beautiful body, so modern writers unanimously agree that a woman should be like a swallow.

That is, because it was the best to have a slim and well-proportioned body type like a swallow.

So? What do you think? was it the best in the world? Or not?

Yes, the Soju writers will admit it.

Hey guys, let's sign quickly!

The Heavenly Sword was the most beautiful in the world, and the small heart was just the hunger of a child!

At this time, there was a sentence that struck the literati of Soju.

This was a book written by Sangwolhee, an unknown writer.

Ivory, also known as Hang-a in her hometown of Qing, was the goddess of the moon, so to speak.

Among the divine beings of Zhongyuan, he was in charge of beauty, and in Taoism he was called the Moon Palace Hanga.

So this was the content of the novel Sangwolhee.

Long ago, Ivory was exiled from the Moon Palace and came down to earth, using the lake where the moon was most visible as a passageway to appear on earth.

That lake was Lake Taeho.

It was a sentence that did not match the historical evidence.

The ranking of lakes in Zhongyuan was as follows: Lake Payang (over eight Seouls), Lake Dongjeong (over seven Seouls), and Lake Taeho (only third in size, less than four Seouls).

The reason why Ivory came down to the half-sized Taeho Lake instead of the larger lake was probably because the writer's hometown was Jiangnan.

Anyway, he was the god of the jar that has appeared in the third lake.

And at that time, Taeho was the territory of the Yue Kingdom, so it was only natural that Sang-a, the goddess of beauty who descended to the human world and embodied beauty, would be the most beautiful woman in the world.

The Wolnyeo, whose exact name was unknown and who was also called AQing because she liked to wear clothes as pale as moonlight, was said to be the incarnation of Ivory.

Sang-a was the daughter of Emperor Shen, one of the Three Sovereigns and Five Emperors, and a minister of Zhongyuan.

Of course, she possesses divine powers, and according to the novel, she came down to earth and gifted the first martial arts to humans, and it was named the Moon Sword.

It was a very fresh reinterpretation of the legend of the Moon Lady.

The highlight of the novel was the meeting between Wolnyeo and Seosi.

A surprising reinterpretation of how Seo-shi, who saw the beauty of Wol-nyeo, became ashamed of his own appearance, and frowned in embarrassment at the world's praise of calling him a beauty!

And the end of the novel.

A long time after the moon girl left the earth.

A peerless beauty wielding the Moon Sword has stepped into Soju.

This was the first return in roughly two thousand years, after welcoming the master who taught the soldiers the first martial arts and personally leading the nation's military, the descendants of his disciples.

A smooth connection from Ivory – Moon Girl – Cheonhwa Sword.

And the so-called hometown mulberry that fills the pride of the Jiangnan people who consider themselves descendants of the Wolnara!

Above all, the value of this novel lies in its sensual sentences, which were unprecedented.

A woman's waist should be thin.

However, there must be five heads.

This was the 5,700-character treatise on the Five Virtues and Five Deities that began like this.

For the Jiangnan literati, this was a shock that turned the world upside down, so to speak!

Also, I was able to see with my own eyes the vivid evidence of the Cheonhwa Sword, and this was what the Jiangnan literati were saying when they gather together.

Hey, have you read Sangwolhee? I read it and was so embarrassed I cried.

My true eyes were blinded and I turned away from the truth. I did not know that true beauty lies in abundance (plumpness). How could I dare to call myself a man of letters and utter such presumptuous words? I cannot look up to the heavens!

I was well aware of the numerous legends of the Moon Lady, but I never questioned why I valued the beauty of the poem more highly than that of the Moon Lady. I am just heartbroken.

It was impossible for a god who opened the way for mankind to learn to be inferior to a mere human, Seo-si.

By the way, have you seen Sangwolhee's sentence?

I haven't been able to sleep since then.

When I closed my eyes, that sentence would come to mind, burning the man's liver and setting it on fire, and my whole body and mind would be filled with arousal, and I would be unable to sleep.

And that nameless man, the three-legged sergeant of Baekho Baekhoso, a member of the direct command of the Shandong Army Commander, was dumbfounded.

"Teacher! You were the pioneer of Zhongyuan literature! Would you please grant me, a scribe, the honor of spending the night debating style and beauty with you?!"

"I have sent a letter to Taeho for you, sir. Please come and give me your advice!"

"I have been enlightened by your excellent writings! They say that the gate has no age, so I, an old idiot, dare to take you as my teacher!"

It's only been two days since I arrived in Soju.

Before selling my military service, I had just submitted the sentences I had been writing here and there to the literary circle, but when on earth did the manuscript turn around and all these writers from Soju rush to see it and be moved by it?

Hey, me? Do I have any talent?

An ordinary person, a common person, would have been arrogant and proud at a time like this, thinking, "I'm a genius!"

This was not the case, for he truly possessed the bearing of a great man, and was qualified to be a great writer representing his time.

"I merely witnessed the beauty of the Heavenly Blossom Sword Daehyeop and transcribed it into words. Even then, my writing was inadequate, failing to adequately capture it. Therefore, your praise was excessive and unbecoming. Please, refrain from it. If you had witnessed the Heavenly Blossom Sword Daehyeop first and had the time to slowly absorb its ultimate beauty, you would have produced prose far superior to my humble work. I merely witnessed it first; I am in no position to receive such praise."

The literati were amazed and thought, "Ah, truly a giant of the times has appeared."

And now it was the era of the Thousand Flower Sword.

The degree to which one can delicately describe the beauty of the Heavenly Blossom Sword will determine the status of a writer.

So, each person thinks of the poem and desperately tries to come up with a sentence.

So, if Qing knew, it was the moment when a grand writing feast would begin, a contest to see who could describe Qing the most likable.

In other words, it's a grand feast of chaos!

But Qing doesn't know.

How could I have known that I would become the star, the moon, the world, the ultimate ideal of the writers of Jiangnan?

Above all, Qing was busy.

"No, why can't everyone do something this easy? Just jump over a wall and you're instantly blasted with energy. was that hard?"

[… … ]

"Should I do the same as Master? If I really push him to the point of killing him and beat him up, he'll know to climax on his own if he doesn't want to die."

[… … ]

"But how can I beat them up again when there's no room for them to get beaten up? San and Nan-gong were already at their peak, so I'll let that go, but even if I beat Zhuge, he'll probably just keep talking and talking."

Now, it was Qing who was venting his frustrations.

Well, where would you find a story like this?

If I had to say, in the Western fable, the king's ears were like donkey ears, and in the current situation, my friends' realm was that of third-rate people.

But the moon in the night sky, which listens silently, was not particularly bright and was a large malevolent star that covers most of the sky.

[… … ]

Countless images flashed through Qing's mind in an instant.

Qing lets out a painful groan.

"Ugh. Wait, stop, I'm about to explode, surrender, surrender. Surrender! Come on, surrender! I said surrender!"

Qing taps the floor with his fist.

But after being kicked out by the extreme pain of the final weapon, Hal (split Hal) about twenty times, it was now a tolerable pain.

It was a really painful experience, like my head was going to split open, but as I kept watching, somehow, I got used to it.

It's not like it's Master's signature honey chestnut, and what could be so hard to get used to when he just plays a scene in his head?

[… … ]

"No, to stop the sword, you need at least some sword energy. Why should I worry about this? Isn't it a given that even a small village has one or two of these? Even the local military officers and ambassadors all know how to radiate sword energy. Why on earth do these guys, born from such good families and blessed with such good blood, still act like they're at their peak, like they're eating elixirs?"

[… … ]

"Well, even at the peak, it's a bit much. It's not like I'm a transcendent being, where every moment was a series of miracles, a record-breaking achievement. So, how can I, a capable person like me, protect you?"

[… … ]

"But they all volunteer to protect me and follow me into dangerous situations. It's just crazy, isn't it? Ah. As expected. This won't do. Hmm. How do I get rid of these leeches? What do you think?"

[… … ]

"Hangzhou doesn't have a mission where you have to stay for a few days, so you just have to go and meet Nyenyeong and you're done, right? So, if I can just get her away for half a day, that'll be fine. Um, should I ask Lan-ah if she has any sleeping pills or something? Or, ugh, ah, wait, stop, ah, okay, I'm going, I'm going, Miss, I'm going!"

Qing's eyes flashed.

No, what do you want me to do? I just asked them to listen to my complaints, so they kicked me out.

So you don't have any friends.

As soon as I came out of the dream, my whole body felt numb.

And um. It's hot.

That's because Murong Zhuxi and Gong Sun-Yaoyi were clinging to each other tightly, each with one arm and one leg raised, hugging each other tightly.

Hmm. It's hot and stuffy.

The blue squirms and slides down with a strange movement.

It was a strange snake-like movement that applies the flexibility of oil liquefaction and the escape method of Shinto.

The place where the blue leaves.

He tosses and turns in his sleep, perhaps because the tall woman he had been leaning on has slipped away.

"Ugh……" "My lady, it stings……"

Two women were muttering something.

As the hands of the two women who were sweeping the bed touched, they immediately began to cling to each other.

As Murong Zhuxi, curled up like a child, dug into Gong Sun-Yaoyi's arms, Gong Sun-Yaoyi stretched out his arms and legs and hugged her tightly.

"Miss Ximen……" "Hehe……"

Qing smiles at the sight of the two clinging to each other.

Isn't this a truly fraternal sight?

For example, she has no friends other than me, and it would be nice if Miss Moyong had someone to hug her tightly.

I think these two will become close friends quickly.

The other two, well, they were really boring.

Anyway, I heard that a lot of people were using it.

Qing sits so quietly and looks down at her friends.

There was only one lamp in the large room, and although it was dim, it was bright enough for Qing to see the scenery clearly.

Soon, Qing's eyes that had been drawing elegant curves began to harden with a serious look, as if revealing some decision.
