\chapter{A Loner's Journey To Solitary Sword (8)}

"Great Master, this Wang has expanded the An-gye today! What a beautiful tactic!"

It was a strategy called the false surrender tactic, to put it simply.

Hanging a white flag to lure the Japanese pirates in was a great tactic of the Saengsaeng faction.

"A great general doesn't go to the enemy; he invites them before himself. Indeed, isn't this skill worthy of being called a master of military strategy?"

"No, why were you going that far……."

"No! According to the Thirty-Six Strategic Planes, this was a trick to deceive the enemy by holding a secret weapon, the sound sword. King Geumjeokgeum, you ordered the general to be defeated first in battle, which was a bold decision to defeat their leader in one move! Also, the general's cannon hidden behind the city gate was destroyed, and the enemy was attacked unexpectedly. You applied three of the thirty-six strategies, so this was the flow of the great plan to truly control the battlefield! This Wang Ssangryong, I congratulate you on your great victory!"

"Hey, it's Mahayana."

Qing was humble.

With the corners of his lips raised in a smirk.

Am I really that great?

Isn't this an easy strategy that anyone who was aware of the cannon can come up with?

Well, it's hard to think first.

So to speak, isn't it like I broke the egg and made it stand up?

How could that be?

How great a master of strategy was Qing.

It's just that the commanders of Zhongyuan lost, and it's a difficult technique to use even if you think about it.

The fact that you surrendered, even if it was a lie, was like a shell that could explode at any moment in the future, and you don't know how long the fuse was wound around.

Even if it's a false surrender, surrender was still surrender.

This was a mistake that can be easily dismissed if the superiors decide to do so, so according to national law, a general who surrenders without fighting the enemy was basically destroyed by adding or subtracting according to the merits and demerits of the three clans.

It was a political and physical threat that could have a devastating impact in the future.

So, generals would rather win than sacrifice most of their soldiers.

There was absolutely no reason to falsely surrender in order to reduce damage.

This was precisely why we need sound and fair politics in our country.

Of course, it was truly a pleasure to receive orders and carry out the work.

Because my soldiers were second only to me.

When you're around Mama, you can freely use tactics that could be used to get you caught, so you could say that Wang Ssangryong's brilliant flattery isn't exactly wrong.

"Okay, this was it."

"Hmm."

Qing looked at the barbarian imprisoned in the prison.

A sharp gaze mixed with a cold anger flew at me, as if the branch had come up late. So, what were you going to do with me? Just look at me.

Qing asks with a mean smile.

"Should I save you?"

The Japanese pirates were surprised by this.

Even Wang Ssangryong was surprised.

"No, Mama!? How could you possibly know how to do this!? My goodness, you were a world-renowned martial artist, and your beauty was also the best in the world! On top of that, your military tactics were like the reincarnation of Sun Tzu! Your calligraphy even puts Wang Xizhi to shame, Mama!! Amazing, wow, this Wang Shuanglong, this was astonishing, on earth, were you truly a divine being, Mama?"

Wang Ssangryong gasps for breath and makes a loud noise.

"General? That's nice to hear, but could you please tell me later?"

"Ah. Yep."

Wang Ssangryong, who had been panting, immediately regains his composure and stands at attention.

Is this general really a great general?

Isn't it too light for a famous person?

"You'll save me?"

"I can give you a chance. I have some questions about your martial arts."

Then the Japanese pirate let out a mocking laugh and then answered in a solemn voice.

"Young Lady, what part were you curious about?"

By the way, the young lady the Japanese was talking about was not Ojou-sama, but Hime-sama, the most respected of all the young ladies in the Japanese language.

Whether it's Zhongyuan or the barbarians, what kind of bandits would have such loyalty in the first place?

"Do you barbarians do this too?"

The blue sparkles brightly, and the starlight shines even brighter in the dark prison.

The expression of the Japanese pirates who were shocked by him.

"Scrutiny! And it's a reasonable scrutiny!"

Ah. I guess there was one.

"Are you, Miss, the swordsman of the license-opening ceremony? Oh my god, there really was a female swordsman!"

"Hmm. I don't understand a single word you're talking about."

However, the eyes of the Japanese pirates were hazy, and somehow, they sparkle with longing, just like the followers of Peng Daesan looking at the Jade Kirin.

But why was the hand so shiny when it's under pressure?

"If the momentum was so strong that it was noticeable, then it was proof of a warrior entering the palace. It was only right to call it a sword pressure."

I heard that all bladed weapons were called kendo, but if you think about it, they were fools who were arrogant enough to talk about swords when they were actually swordsmen.

It refers to a weapon with blades on both sides, but if everything with a blade was a sword, then was a razor also a sword?

They're funny guys, anyway.

So, I asked about various Japanese swordsmanship, or more precisely, Dojutsu and Hankenjutsu.

And then the martial arts window sparkled.

Qing, who checked the list, was astonished.

Abstract (dagger). Blue border.

What the heck? You uncivilized barbarians, no, you uncivilized Japanese bastards, no, miss, look how these derogatory terms stick to you when you live in Zhongyuan.

Anyway, do foreign martial arts count as martial arts?

But if it's blue, it's third-rate among third-rate.

It's just trash with a white border barely visible.

It was a sad story for the barbarians the Japanese to hear.

But it was a natural fact for Qing.

Why, even when playing video games, they were often just materials of the two lowest grades, and even then, considering the consumption of other goods, they were so inefficient that they were treated as unusable trash.

In any case, the fact that the martial arts window had appeared meant that this Japanese pirate had told only the truth without lying.

In fact, the Japanese people's habit was to truly respect the strong and bow down to the strong, so they do not even dare to think of discussing lies in front of the great swordsman who has reached the level of reason.

But in Qing's eyes, he can still see the ugly trophies the Japanese man was wearing around his neck.

I've felt it before, but seeing that each person collected different parts, I can tell that the people they harmed were all in pieces, with not a single healthy part left.

Well, I guess I have to keep my promise.

"Well, a promise was a promise, so I'll spare you, okay?"

And Qing's smile becomes brighter and brighter, and the corners of her mouth become wider and wider, reaching her ears, taking on the appearance of a wicked, grinning devil.

"Since I'm going through all the trouble to keep you alive, shouldn't you live a long life?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Any city in Zhongyuan was bound to have at least one old tree that was said to be wise.

In Yeogo-hyeon, there was an old zelkova tree standing in the middle of the city square, its huge trunk hanging down.

Under a large tree eight zhang high, a thick rope was tied around the trunk, which was two zhang in circumference, to tie a leash to the animal.

They were strange-looking beasts.

At first glance, it looked like a human, but its hair was oddly shaped, and its limbs had joints that seem to be in the dozens and were wobbly.

When it made a strange howling sound, it opened its mouth wide and had no teeth. What kind of rare beast was this?

So there was one large poster.

\begin{quote}
"Please refrain from the following actions:
\medskip

The act of kicking with the foot, punching with the fist, or hitting with a tool, etc.

The act of throwing a hard, heavy object and hitting it.
\medskip

It is okay to just throw soft food like filth or rotten food at it.

If you want to see the beast's antics out of personal resentment, let's just pour a cupful of boiling water on it.

Not only your grudges, but those of your neighbors are also precious.

Let us all take good care of each other so that the beast can live long and not die without suffering.
\medskip

- Heavenly Blossom Sword Ximen Qing's compensation.
\end{quote}

It was a truly terrible phrase to stick on top of a body that has had its limbs smashed and its teeth pulled out and tied up.

And then you put your name on it and say it's something to be proud of?

In fact, even her friends and Wang Ssangryong tried to dissuade me.

Is it really necessary to reveal the cruel and heinous deeds by revealing their names and actions?

But Qing was stubborn.

Even if you call it a compromise, it's just that orderly Yang ghostwrote it because he was afraid someone would steal it if it was a precious piece of writing?

Because if anyone were to ask about grudge, it would be directed at her.

Even though it was supposed to serve as a safe screen, who invited the military? It was Qing himself.

Who was it that insisted on firing a cannon when they were trying to drive them out gently? It was Qing.

And what.

If the rumor spreads far and wide, the Japanese pirates might want revenge, though I'm not sure if they have that kind of loyalty as a group of thieves.

If something like that were to happen and the Japanese pirates would vent their anger by needlessly harassing the civilians, wouldn't it be better to reveal that their enemy was here and reduce the damage?

Anyway, after this work was over, I plan to return to my sweet home in the western part of Hubei, deep inland.

What could those Japanese pirates do?

However, there were only a few who frowned, and those who did were either outsiders who came to see the sights or those who still had lingering feelings for the magic explorers.

After all, there was not a single person who lived near the East Sea that did not hold a grudge against the Japanese pirates.

If you expand it to include not only yourself but also your family, relatives, neighbors, and friends, you have probably lost at least one person to the Japanese pirates.

"You Japanese bastards, you filthy bastards, it was my eternal regret that I cannot personally sever your breath. Listen, please give me a cup of that boiling hot stuff."

"Yes. Here it is."

There's even a stall nearby boiling water, so it looks like a business that's taking advantage of people's resentment.

He looked quite vicious for a businessman.

Amazing fact.

If a person has no nose, his or her impression becomes dirty.

Everyone in Yeogo-hyeon knew that this person was a survivor of a village that had been annihilated by the Japanese pirates.

So it was not surprising that he uses his own money to buy firewood and boil water to provide it for free.

He has a grudge to that effect, I suppose.

So the passerby spits, takes the glass, and pours it over the beast.

The porcelain cups of Zhongyuan were high-quality wine glasses, thick cups used to pour and drink strong liquor.

Of course, since it was a luxury item, the wooden cup used by the noseless man was just a replica, but in any case, the capacity was similar.

The amount was exactly the size of one large spoon, so even if it's boiling water, the amount was really tiny, like the size of a rat's tail.

But it still hurts when the boiling water touches the body.

It hurt a lot.

Although the amount was small and you pour it slowly, boiling water still hurts even if you pour it slowly.

"Kuaaaak! \#\#! \#\#\#\#! \#\#\#\#\#\#\#!"

The beast was howling, but no one can understand what it was saying, so no one can understand it.

If there had been a request, it would have been possible to interpret that he was begging to be killed.

If you writhe in the heat, the pain of moving your shattered limbs increases a hundredfold, a thousandfold.

The noseless man croaks as he looks at the sight, but his face was bright with a smile.

As the sight of those beasts writhing piles up, one by one, I feel as if my stuffy stomach was being relieved.

So the man looked at the tree again and sees the poster attached to it.

\begin{quote}
	Heavenly Blossom Sword Ximen Qing
\end{quote}

The man engraved the six letters of the nickname and name into his mind for a long time.\footnote{'Heavenly Blossom Sword' is three characters/ Hanzi long, while 'Ximen Qing' is also three Hanzi long}

He was a dark-sighted man who knew only a few letters, excluding numbers.

But now he could at least write six letters nicely.
