\chapter{A Loner's Journey To Solitary Sword (6)}

In fact, the military of Zhongyuan did not fulfill the military duties that the Qing thinks they should.

In Qing's homeland, military personnel seem to be tasked with protecting the country and its people. But what about the military personnel of Zhongyuan?

The military of Zhongyuan was only there to protect the imperial family, the emperor, and the lands owned by the emperor.

People?

Do you know how many people were there in Zhongyuan? Do you have to protect them all?

After all, the people were like animals; if left alone, they will prosper and grow on their own.

Anyway, inland there were bandits, and on the coast there were bandits. If we were to be precise, these marauders would appear every single day of the year, 354 days a year (a year in Zhongyuan was 354 days).

So what's so special about being a Waegoo?

If I had to say, it's like a pest like a locust, so no matter how much you catch it, there's no end to it.

So, if the soldiers who were supposed to serve the emperor and prepared for battle were chasing after these bandits, when on earth will they be able to train?

Above all, the greatest duty and most important task of the military was to farm.

But even so, there was a reason why Wang Ssangryong was sweating profusely, no, gushing sweat.

It was absolutely, absolutely not because my inner conscience appealed to me that it was wrong to act in a way that did not protect the people with universal morality.

I simply took it as a rebuke for allowing those dirty barbarians to invade the land of Zhongyuan and trample on the land of the solemn emperor.

By the way, it was okay to invade the sea because the sea was not land.

In the past, people were not allowed to go out to sea, let alone live near the coast, and this was called the Haegeumryeong.

They were taken away about a hundred years ago, and now they can build houses and live on the beach and engage in fishing, but they have to be prepared for the plunder of Japanese pirates.

Anyway, Wang Ssangryong desperately tries to come up with an excuse.

My head, which was usually spinning smoothly, was creaking at times like this, and with Qing's eyes looking unkind, I was left feeling blank and dizzy.

A ray of light shines at that moment!

"Still, the commander's words aren't wrong. I heard Shandong is relatively safe. However, I heard that because Shandong had established coastal defenses, the Japanese invaders flocked to Jiangsu Province and suffered significant damage."

Nan-Gong Shencai supports the commander.

The city official looked at the Grand Duke of Nan-gong with a moved face, but Nan-Gong Shencai simply said what he knew and had no intention of taking his side.

He didn't have the political acumen to do that, and even if he had it, he'd rather erase it and invest it in swordsmanship.

"That's right. Shandong, which was originally the most noisy, was now quiet because all the Japanese pirates have flocked to Jiangsu."

Gong Sun-Yaoyi adds in a cold voice.

Since it's her neighborhood, she couldn't help but being sarcastic.

Come to think of it, wasn't that general the one who pushed the Japanese pirates to Jiangsu Province?

Thanks to this, there were twice as many Japanese pirates in Jiangsu Province.

"Oh. was that so? Hmm."

Qing's eyes were restored to their original state.

Since it was in front of Gong Sun-Yaoyi, I cannot take his side and say that the general was not at fault.

In any case, isn't it true that the general also prepared his own defensive measures, such as deploying a fort or something along the coast, and that they were very effective?

The Shandong General must protect Shandong, so there's nothing he can do about the territory of Jiangsu Province.

Hmm. As expected, he's a master! Looks like he really was a master.

In terms of the video game Romance of the Three Kingdoms, he was Wang Shuanglong, a man in his nineties with political power.

Politics also greatly relieved Wang Ssang-ryong, who quickly interpreted Qing's gaze.

The truth was this.

Rather than preventing the invasion of Japanese pirates, wouldn't salt and seafood be produced if fishing was added to the barracks of the military camp?

It was a moment when a similar embezzlement to put excess profits in one's own pocket helped overcome a major crisis.

Although the general's intentions were extremely impure, it was true that the result was a significant decrease in the number of Japanese pirates and their activities became quiet.

Truth and facts do not always coincide.

However, Wang Ssangryong was determined to order the cannons to be fired when they discovered any enemy from now on.

This was a very big decision.

Gunpowder was expensive, and surprisingly, even military gunpowder has to be purchased out of own pockets if used beyond the basic, meager supply.

It was a tearful spirit of love for the people that accepted the loss of profits from selling salt and seafood.

Anyway, that's it.

The expressions of the soldiers setting up camp inside the castle walls were bright.

I'm beaming at the thought of getting up early and having some drinks and passing out tonight.

As the army followed the innkeepers, the innkeepers raised their rates and the private houses emptied their bedrooms, smiling warmly at the prospect of a long-awaited influx of public money.

Anyway, Wang Ssangryong steps forward to fulfill his duty and receive Jihyun's hospitality.

When you don't have friends, you get treated and played with, but when you crowd around like this, it's fun to just walk around and wander around.

Wang Ssangryong didn't even bother to ask His Majesty to come with him, because His Majesty wouldn't be the type to accept Jihyun's hospitality over her close friend.

Among the positions that govern the city of Jihyeon, he was the lowest-ranking official, and was of the same rank as the Taoist priest and the Vice-Minister who Wang Ssangryong treated like a common servant, so wouldn't their ranks have been different from the beginning?

So, first, let's take a walk around the city.

Peng Daesan, who usually goes for walks, follows along without a word.

There was no need to explain why the army of women who were trying to find lodgings hastily turned back and followed them.

When asked if there was anything worth seeing around here, Zhuge Lixian gave a firm answer.

"No, Sister."

"Huh."

"With the Japanese pirates causing such a volatile situation, wouldn't you just quietly return home after dark? Even if there were things worth seeing, the Japanese pirates wouldn't let you stay still. That's why this village, so close to the sea and by the river, was like this."

Why would those bastards walk or run on water when crossing the sea?

If that happens, there will be no need to go through the trouble of crossing the sea and plundering to establish a religion.

But? There aren't any warehouses worth plundering along the coast.

And since you're coming in by boat anyway, you're just coming in by following the river.

"Then, what if we sink the ship?"

"Just by looking at the ship, there's no way to tell if they're Japanese, merchants, or fishermen. And there's no army that would use cannons, right?"

"Hmm. This was a mess. Seriously."

I know that the security level in Qingdo Jungwon was not that good.

Even when I was a beggar, I saw all sorts of things happening in the middle of the night in the big houses of the big city. And even if I didn't go far, when I rode in a carriage with Xue-i-ri, didn't I head towards the bandits without a fight?

What's more, they were barbarians, not people from Zhongyuan.

However, if there was something you don't understand.

Why, aren't they Japanese?

You came here by boat from Japan?

Even on a ferry or something?

Does that make sense?

In this primitive age, we don't have cruise ships, cargo ships, or any other massive shipping technology.

But that question was soon completely resolved.

"Why were you here!" "Why were you here!"

If you mention Cao Cao, Cao Cao will come running in a hurry. was it because Qing, who has already been scolded severely, was still not careful with his words?

But the civilians who shout like that don't look particularly afraid.

Because.

"You damn Japanese bastards, ugh, this time you got the date right."

"I knew those kids would strike back at some point."

"It seems that the heavens were not indifferent either."

"Huh. How naive. Even then, they'll just scare them away. Do you think the soldiers will step forward? And if they do, will they really back down? They'll just pretend to retreat for a moment, and then when the soldiers withdraw, they'll attack."

Qing glanced around at her friends, nodded to each other, and then they all stamped their feet on the ground and headed towards the castle wall.

It's just the poor soldiers who were being made a fuss for no reason.

As they were about to have a nice drink, the Qing party passed the military camp where an unexpected commotion was taking place and climbed up the castle wall.

The female soldiers on the wall look at him as if they were wondering who the martial artist is, but they do not try to stop him because they were afraid that he might help them.

In the first place, when it comes to the Japanese pirates, the martial artists were more willing to help than the government, so they receive friendly, reassuring looks.

Qing looks at the authentic Japanese pirates.

What the heck was that thing?

First impression was that it was small.

And it's dirty.

The beard was messy, shaved white from the forehead to the crown of the head, giving it a strange appearance.

You leave your beard alone, but do you take care of your bald head?

And yet, he let his hair, which was sticking out from side to side, down in an unsightly manner.

There's a beggarly outfit there, no, worse than a beggar's outfit.

They wrapped themselves in dirty, worn-out cloth, and some covered their torsos with wooden armor.

Then Qing frowns sharply.

Thanks to this, the tip of the black vagina dangling from one of the ten lower bodies that was roughly covered by the cloth was not exposed.

Just as the hometown of Qing was not called Seongjin for nothing, it seems that there was no culture of wearing underwear in the past.

But would she be so naive as to frown at the sight of a man's glans?

Not because of that, but because of the monsters that they proudly wear around their necks and on their arms.

Decorations made by piercing severed ears or noses, fingers and toes, and even the scrotum or breasts.

These kids don't just plunder.

Usually, such symbols were made and worn by them to show off to each other, and they mean that they were a species of human beings who hunt people and take their spoils.

What Qing saw very accurately was that this was the characteristic of the orthodox Japanese pirates.

The Japanese equate cruelty with greatness, and they consider it a natural right for the victor to massacre the vanquished.

Thanks to this, the Japanese's collective punishment system not only binds the tribe but also the entire village.

The reason why the Japanese people were so keenly aware of each other's feelings and thoroughly reject those who stand out.

This was also the reason why we obey the strong like dogs.

"Open the gates and surrender immediately! And bring fifty women under the age of twenty. Then I will show special mercy and take only half of the storehouse!"

"Isn't that Zhongyuan dialect? You speak it really fluently."

"Sister, I'm sure he's a Zhongyuan. He's about a span tall, and he's wearing a helmet to cover his head. I can't do that horrible Japanese hair, so I'm wearing a helmet and pretending to be a Japanese."

"Huh? You're from Zhongyuan?"

"How could the Japanese know the geography of Zhongyuan before invading? That's why there were such lackeys who collude with the barbarians."

The more you know about Zhongyuan, the more astonishing it becomes.

Qing looks down at the Japanese pirates.

About three hundred?

Three hundred was certainly not a small number.

In a small city like this, isn't it all about one hundred lakes and one hundred and twenty soldiers?

There were constables, but they were not military officers but rather scarecrows who were not really capable of fighting with force.

So, he stands before the gates with such confidence and threatens to surrender.

Qing looks at the savages and asks again.

Certainly, it's convenient because Zhuge was there.

"Zhuge. Do they also use martial arts or something?"

It feels like this was the first time I've encountered foreigners from a different civilization, other than Zhongyuan people or barbarians (local people).

The mysterious cosmic energy may not be limited to this primitive ancient China.

Still, I wonder if they also have some kind of superhuman skill that allows them to run wild.

"I'd probably call it martial arts. "Sul" refers to mystical things like sorcery and magic, so to call martial arts "mysterious" would be an uncivilized, monkey-like intelligence."

If you listen to Zhuge Lixian, you will realize that he was a great man who secretly has a deep contempt for barbarians.

However, this was a natural quality for a person from Zhongyuan at that time, and in reality, the difference in the level of civilization was also huge, so it wasn't really wrong.

"I'm not a formally established practitioner, but as with any martial art, I probably possess some internal energy in the form of a pupil. Oh, do you know what a pupil is? A pupil is—"

"No, I know that much, don't I? I'm a martial artist too? I'm even better than Zhuge. Do you think the ultimate achievement was achieved through some mahjong game?"

The pupil was a primitive ancient axis.

As the study of martial arts developed, it was proven that it was much more efficient to have my maternal grandparents study and my own study separately.

So, today's warriors learn both weapon techniques and internal energy techniques separately and practice them simultaneously.

But if you practice martial arts diligently before that, you will realize that this was possible!

Before you know it, your internal energy will have accumulated!

I don't know why, but anyway, it's really amazing.

This was the original internal energy method, Donggong.

This was the standard for how many years of internal energy was used in the past to measure the amount of internal energy.

Roughly speaking, one gapja of internal energy was equivalent to sixty years, which means that it was equivalent to sixty years of gathering energy without meditation in ancient primitive martial arts.

Nowadays, when you were at your peak, it was roughly equivalent to one year of internal energy, and even if you say sixty years' worth, it was an old saying and there was no exact standard, and the amount of internal energy consumed varies depending on the type and nature of the martial arts, so it was not necessary to mention the total amount of internal energy, so it was not a unit that was used anymore.

So Qing looked at him blankly.

A quiet evil expression spreads through his eyes.