\chapter{A Loner's Journey To Solitary Sword (12)}

There were Four Heavenly Kings in Zhongyuan who were famous for their poetry.

Li Bai, Du Fu, Wang Wei, Su Dongpo.

Li Bai's nickname was Poet Immortal.

Du Fu's nickname was "Sicheng" (Poet Saint).

It's just that he doesn't seem that strong because of the liberal arts atmosphere, but what if he were a swordsman?

Swordsman! And Sword Saint!

This way, we can understand at a glance the positions of these two in the literary world of Zhongyuan.

Wang Yoo may be wronged.

Wang Yu was also good at writing poetry, but he was pushed aside by the appearance of two monsters at the same time.

Wang Yu's nickname was Shi-bul (詩佛), the real Shi-bul.

The nickname of the contemporary poet Ha-in, who was not even included in the Four Heavenly Kings, was Shi-gwi (詩鬼), but Shi-bul (시불).

However, in terms of martial arts, compared to the Sword Master and Swordsman, the Sword Spirit and Sword Ghost were of lower level.

One could say that Su Dongpo, who was three hundred years younger than him, still gave him a nickname as a courtesy to his senior.

Su Dongpo doesn't have a specific nickname, but if I had to give him one, it would be Su Dongpo of Dongpo Pork.

I don't know what the tastes of the Hangzhou people were, as they called it Dongpo Pork and Su Dongpo Meat, because it was a meat dish made by Dongpo.

And the destination of the Qing Dynasty was Hangzhou, the hometown of Dongpo Pork, and they were running towards it.

So, if you were a glutton who couldn't resist your natural appetite, you would have been able to run away happily.

Dongpa-yuk, wait, I've found everything, haha.

But Qing's heart was cold, and the sound of the wind blows deafeningly, the calm before the storm, I had a drink…

Ah, the rough and rugged road.

The path was more difficult than soaring into the sky, as the touch was difficult.

On a road that even a yellow crane cannot cross and a monkey cannot hang on to.

I sighed, sweeping my chest and sitting down, wondering when you will return from the west.

Only sad birds cry in the old trees.

Because the path of reaching the sky was more difficult than reaching the horizon.

He turned to the west and just let out a long sigh.

It was an unanswerable victory.

The poem by Lee Tae-baek was a poem of the same name.

It was not that he memorized it because he liked it, but rather because Ximen Surin, who knew that his disciple's handwriting was extraordinary, forced him to memorize it and instilled it in him.

And since it was knowledge that was forcefully instilled, the parts that didn't interest me flew away.

So, it ended up being a short poem that was half-cut and half-truncated, with only the memorable parts put together.

This poem has many different interpretations.

There was also a story that when Lee Tae-baek entered Sacheon, he was so angry and speechless at the sight of the rough roads that he wrote it.

There was also a saying that the difficult thing was not the skill itself, but the precarious tightrope walk of life in office, where superiors were nagging and subordinates were pushing.

But it was always the case that poetry was created and reaches people's hearts.

Other people's interpretations were of no use except for scoring.

Huh, the original author? What do you know about the original author?

To Qing, it wasn't hardship, but loneliness, and the road she walked alone must have been difficult.

It's not that the path was steep, but that if you're going alone, it's going to be difficult, even if it's a flat, well-trodden road rather than a precarious path on the edge of a cliff.

Yeah, that's right.

No matter how difficult the path is, if there was someone to walk it with you, what could be more difficult?

The swords were like this and the rocks were like this, the fucking mountain path was really dirty and dirty. They're pushing and pulling each other while giggling. Put your hands away, let go, won't you get up? Kill me instead. The base was in the mountains. Leave me alone and go. Then live here. Cheer up, fighting. I could have just happily gotten through it.

In Buddhism, it was said that all the landscapes that people see and draw come from their own minds.

So, on a bright moonlit night, it might be a good thing to be lenient about Qing's performance.

Oh, look at the moon, it's so pale and lonely, it's because it's all alone.

The reason why that ugly star in Cheonsalgoseong was all twisted up was because people, or rather, the star, were left alone.

Look at that parasitic spirit of the Thousand Horses. It's been waiting for hundreds of years in the empty crystal horn, waiting for its next body, so people were going crazy.

If Qing's friends heard this, they would rub their arms with goosebumps and ask in horror, "What's wrong? were you hungry?"

If Ximen Surin had seen it, she would have been furious, saying that a girl who knew that was crawling out in the middle of the night and running alone was the one who had to do it.

But Qingdo didn't just come out without thinking.

According to the general, the distance from Suzhou to Hangzhou was about 300 li, and it was a flat lowland with not a single mountain ridge blocking the way.

If you were Qing, which could be considered the best in Zhongyuan in terms of lightness, you could run without stopping and arrive in roughly an hour and a half.

The promise I made with Yun Yuanying was that we would stay three nights in each city we passed through and meet in the best room at Hangzhou Jeil Guesthouse.

So why don't you just go quickly, see Nyong-in's face, and then come back?

Of course, they did mobilize the military.

In the first place, there was no need for Yun Yuanying to come alone, and rather, wouldn't it be better to have an assistant?

After saying that.

Excuse me? I said it was okay to have an assistant, but even so, isn't 1,230 people too many? What were you going to say?

And it's not that Qingdo doesn't believe in it.

Qing was sensitive to favors.

How could Qing not notice the boundless, unidentified affection that Yun Yuanying was sending me?

So, I ran wild using the five zombies that were given to me at Dongjeongho.

Wait, come to think of it, it was Dongjeongho back then, right?

This time, it's Hangzhou, famous for its West Lake.

Could this be a water disaster?

If there's a famous lake on the way, I'll have to avoid it.

Anyway, if I had decided to cause trouble this time, it would have been difficult.

Even in the Wulin Alliance, it's easy to get there by canal.

If only I had asked for help from nearby people like Little Hwangbo, Little Mo-yong, San-i, and Tteobori, they would never have turned me away.

Thinking about it that way, Qing felt sorry for Wang Ssangryong.

Well, even though I'm a government official, I did something a little reckless.

If there had been even one ignorant person who ignored the inviolability of official duties, how could those weak soldiers have endured?

Fortunately, they're all cowards, so the military can't touch them and it's okay. What if they see blood because of me?

Anyway, Yun Yuanying was safe for now.

He's not the type of person to say things like, "I laid a trap there for no reason and finally caught him," or "How dare you interfere with the work of the Blood Cult?"

But that's the problem.

Isn't that the kind of girl who suddenly squirts human blood and clings to it, saying, "This tastes so good!"?

One day, out of the blue, my appetite changed, my blood sugar went up, so from now on I'm going to drink only zero-calorie drinks, so it wouldn't be strange if I suddenly turned around and said, "I don't need you anymore."

As if I had suddenly fallen into this world, one day suddenly-

Good idea, good idea. Yeah, my heart, my pale heart, my soft pale heart. Hmm. I miss my pale heart. Ah, so tender, so tender, so tender, so bright.

Qing grits his teeth and increases his speed.

The blood vessels began to ache faintly from the excessive release of internal energy, and even that strong body protested, saying, "You bitch, please move a little more moderately." The heart pounded, the blood pressure pounded against the blood vessels, and the overworked lungs squeezing the pain that seemed to be squeezing, tormented their master.

Still, it's better to be sick.

Exercising one's body when one was mentally unstable was a basic human defense mechanism.

How long did it take to run like that?

Sweat pours down like rain, and when you lick your lips, it feels like you're covered in salty, sticky sweat.

Sweat drips down my eyebrows, which have lost their waterproofing ability, and I frown as sweat drips into my eyes.

A pain that feels like it's squeezing and shrinking my whole body.

My heart was pounding so hard it hurts, my lungs want to be ripped out and thrown away, and my throat hurts as if it's been scraped with a nail, phew, I can't breathe.

And then, before I knew it, there was a light in the distance.

As the best entertainment city in Zhongyuan, they open night markets outside the city walls at this time of night and light up lanterns to do business.

Before development, it was a wetland, and even now, Hangzhou was a low-lying land with a lot of moisture.

Since I can't go into the city like this, I throw myself into the tall bushes and run.

"Ugh, uh, uh, ah, kk, uh."

My back was damp, and as if I was lying on soft ground, a chill ran down my hot body.

Amazingly, the rebound from long-distance running comes after you stop.

What if you feel like you're already dying while running?

If you stop, you will fall behind.

Qing lies there for a long time, gasping for breath.

However, the body that transcends humanity also has resilience that transcends humanity.

Qing, who had been lying down for a while, raised her body and slapped her butt.

"Oh, it's damp. It must be the ground."

It's not that it's not true, but if someone saw her back, they would probably scold her for lying on the mud floor.

Anyway, I'm soaked in sweat, so both the front and the back were damp.

There was a difference of the degree to which the front was lukewarm and the back was cold.

"Whew, ah. Right."

Qing spread mud on his face.

It smells a bit, but isn't it still the mud beauty that other people pay money for?

Anyway, thanks to my constitution, my skin would be fine even if I spread mercury instead of mud on it. Well, then would I be fine even if I spread something like radiation on it?

Well, there's no way to know.

Qing enters the night market.

The clothes were completely soaked and clinging to him, revealing his unique body shape, which was unrivaled even in Zhongyuan.

But no matter how voluptuous a body is, what if it has mud thickly smeared on its face?

People were slowly making way.

It's not that the mud-covered appearance was strange, but rather that there were people like this who originally roamed around Zhongyuan.

That's a bitch.

Move, don't come near.

Phew. You dirty little bitch.

In all civilizations, including the East and the West, leprosy patients were treated in this way.

"hey?"

"Can't you just get out of here? What unlucky thing was this leper woman doing on such a good night? Hehe, why were you looking for me?"

The merchant, who had been frowning fiercely, immediately changed his expression and bowed.

Kang Ki-ran, whose hand sparkled brightly, would turn even the most rude person into a kind person who was kind even to a leper.

"Please give me a hat to cover my face."

"Oh, yes. Okay."

As Qing picks up the coin, the merchant shakes his head cowardly.

The merchant frowns at the coin as if he was looking at something dirty, then answers with a forced smile.

"Hehe, just take it."

"Well, yeah."

It seems like he doesn't want to take the donkey's money.

Hmm. That turned out to be a shame.

I'll remember to give it to you later.

As Qing stared intently at the merchant's face, trying to remember it, his face turned even paler for some reason.

Qing presses his hat down deeply.

There's no way you could pass through the gates with mud on your face.

Even in the middle of the night, the city gates were wide open, the streets were bright, and there was no darkness.

The guards were also leaning against the wall, watching the splendidly dressed women with excitement.

Then the guard looks in Qing's direction.

But a female warrior with a huge sword and a covered face was suspicious enough, but what good would come from messing with a martial artist?

It wasn't that uncommon for martial artists to act strangely, and unless they were plagues like leprosy, the guards wouldn't have any reason to stop them.

"Excuse me, but I have a question. Where was the inn that was famous as the best in Hangzhou?"

Rather, the suspicion fades even more when he calmly asks for directions.

Suspicious people try not to stand out, so they don't ask guards for directions.

Besides, there must have been more than one or two martial artists who asked for directions, saying that someone with divine power was coming to Hangzhou Jeilgaekjan.

"When we say 'Hangzhou's best hotel,' we're talking about Manwoljang. Follow the road to West Lake, and you'll know it immediately."

"You can tell when you see it?"

"If you look, you will know."

No, you know when you see it?

Qing was dumbfounded, but the guard's tone was too firm for her to complain about the unkindness.

Because it seems like you're stating something very obvious.

So, Hangzhou, West Lake, in front of Manwoljang.

Qing mutters without realizing it.

"You'll know when you see it for real……"

Of course, there was a gilded pavilion standing alone, how could you not recognize it?

It was a dazzlingly bright building with hundreds of lanterns that seem to have been lit with great difficulty.

So, anyone can see that it was the best hotel in Hangzhou.

So Qing strode forward.

I'm going to meet you now.
