\chapter{A Loner's Journey To Solitary Sword (5)}

Surprisingly enough, sleep was not a very important issue for martial artists vehicles.

Although it was not a method that one likes, with a practical compressed meditation, one can postpone fatigue and weave the mind clearly.

Of course, it's a temporary measure, if you do that every day, it's easy for people to go crazy.

You should get a good night's sleep at least once every five days. If I had to say, it's more like a trick to postpone fatigue.

This could be said to be the biggest difference between civilians and civilians.

How efficiently can we use the same twelve o'clock time for everyone?

However, in reality, there were not many drones who do this. One in ten? One in a hundred?

Unlike the Qing homeland, in the primitive and ancient Zhongyuan, there was not much to do after the sun set, and not many people practiced with such urgency and intensity.

So, in that sense, the Half-Geom Ssangdohoe can be said to be a very healthy club for true martial artists.

Even if we assume that Gongsun Yo-ye, who carried out his family's long-held wish as if it were natural, or Nan-gong Shin-jae, who had a strange belief that if he built up his internal energy at night, he could swing his sword once more during the day, were characters who had always done so.

Since the Qing Dynasty entered its peak, Peng Dashan has become more venomous and sincere, Murong Zhuxi (who had trouble sleeping at night, but that was how it looked to others), and even Xue Iri, who was as venomous as ever.

However, Zhuge Lixian, who believes that you need to sleep well for your muscles to grow well, was terrible at sleeping, and Tang Lan-Ah was not interested in martial arts.

So, in the eyes of Peng Ga and Mo Yong Ga, how could our child, who was friends with Heavenly Blossom Sword, become so special?

As they say, you need a rival to grow.

As was often the case with older people, the elders of the family never fail to brag about their children.

The name of the strangely named training club, the Half-Geom Double Sword Club, cannot help but be high.

There was a reason why Mucheon-gak, which was used to host the highest-ranking guests of the Wulin Alliance, was given to us, even if unofficially.

Anyway, sleep isn't really a big deal.

But that's the kind of thing it is.

After soaking in the hot water, I came back to find four women spread out on the bed.

Originally, the higher the class, the larger the bed, so the space was spacious, but somehow, their eyes were sending each other an appeal to come here.

Qing was strong against curses, fists, and swords, but he was weak against this kind of warmth and was the type that cannot use his strength at all.

Even if you go between the two, there were two people on each side, so the remaining two will be upset, right?

"Um. Guys?"

"What were you doing? Why aren't you coming here?"

"It's here."

The small, long things at the left and right ends urge the blue to sing.

And the other two will come here too, he said with bright eyes.

Hmm. Proving friendship was really difficult.

Are you really friends only if you share a bed?

Qing tries to establish fairness in his own way.

"Since Nan-Arang and Mo-Yong slept together yesterday, I'll sleep with Ye-Rang and I-Ri today."

Then Nan-a got angry.

"Where's that? Qing, how could you do that to me? were you telling me outright that you'd sleep with any other woman besides me? Tell me straight. was it me or them?"

"It's not even a child……."

Even Mo Yong-ju-hee, who can only sleep comfortably and soundly with Qing'er by her side, doesn't like to sleep alone.

So, I'd like to propose a mediation plan.

"Uh, why don't we just sleep together?"

So, formation number one.

Four people lay down, one in the middle and one on each side of the square.

"Hmm. was this right? Heh, can you stop tickling my feet? Who's pulling my hair?"

"They're holding hands."

In other words, if the blue dragon stretches out like a large dragon, it was said that even if it can hold the left and right sides with its hands, it was not enough to hold it up and down, so it grabs the feet and hair.

So this time, Jinhyeong.

Xue-i-ri on the left, Gong-sun-yo-ye on the right.

There's a dangnan on the boat.

And behind him was Murong Zhuxi.

It's not hard to find your center because of the two people sticking close to your left and right.

"Is this right, Miss Moyong? were you alright?"

There were two people above me, Murong Zhuxi.

Even Qing was a head taller than Murong Zhu Xi.

"Ugh, this, pressure, I'm okay."

"Then it's solved. Okay. He's okay too."

"How could it be okay? And what if I'm not okay? What the hell was this?"

You'll have to keep your balance the whole time you sleep, your chest will feel a dull pain from the pressure of your head on it, and your back will feel like it's gasping for breath with a sharp pain in your chest.

In fact, it was difficult to say that a drone can withstand the weight of two people, but the case of it secretly continuing to press down must be considered separately.

Even if I can tolerate it a little, if it's like this in the first place, it's going to be too uncomfortable for Young Lady Moyong.

"No, my lady, I'm really, okay. Phew. Just the right amount of pressure, phew. I'm fine being under you, my lady."

"No, Miss Moyong was the same. What if I just say it's okay? If you have something to say, say it directly. You have to say it outright if it makes you uncomfortable. If you just keep trying to accommodate, it'll only hurt your feelings."

"No, I really like it this way……"

"Don't do that. Come on, everyone, wake up. This isn't right."

So, while Murong Zhuji was crying, Jinhyeong also broke up the plan.

"Okay. Yesterday I slept with Miss Moyong and Lan-ah, so today I'll sleep with Ye-rang and Iri."

"What? I can't admit it, no, I won't!"

"Even if I try hard, it won't work?"

"Sigh, how could Qing'er do this to me……"

"Pretending to cry was no use."

"No, look at that girl! She's so full of energy! How can I sleep alone with someone like that?"

In response, Xue-i-ri makes a fist with her thumb and little finger outstretched, a gesture used in her hometown to indicate a phone call.

For reference, in Zhongyuan, this was a hand gesture representing the number six, and was used in a childish way to mean, "I am great," or "Am I great?"

When someone was great, it can be seen as a compliment, but because of the nature of the people of Zhongyuan, praise was something that must be treated with great fanfare, so it was said that it was not often used except among very close friends.

"Write, then you can't write like this."

"I didn't do anything."

"You showed all your hands, didn't you? were you lying now?"

"no."

Xue-i-ri slowly avoids eye contact.

I think these two need to become closer.

"This won't work. For today, let's just sleep with Yerang and Iri, and starting tomorrow, we'll split into two groups. Nan-a and Iri will be in one group."

"What!? Why me?"

"no, I do not want."

"It's my choice. If you don't like it, I'll just sleep with Yerang and Moyong."

"Tch."

"No."

"Decided. So what were you going to do?"

Tang Lan-Ah and Xue-i-ri stare at each other fiercely.

Then, at some point, there was an unspoken agreement, and at the same time, a sigh of relief was expressed.

"Young lady? Uh, it's okay if we all sleep together, but I'll support you from below, so how about you take turns getting on……?"

"I'm uncomfortable too. I need to sleep soundly when I sleep. But still, Miss Moyong has become quite the person."

"yes……."

In any case, Lady Moyong was a representative of a faction within the Yongbong branch, so she was a worthy mediator, or perhaps a bright person.

Then the little girl tilted her head.

"There's something about him too, he's really suspicious…"

Anyway, it's a sudden formation of a comrade group, but the more I think about it, the better it seems.

While I'm at it, I'll make some more friends.

If it's someone like Miss Moyong, it's fine since she's upright.

I think Nan-Arang and Iri were too difficult for Gongsun So-Jeo.

To begin with, neither of them have any friends.

No, among the female members, there was no one who has a friend other than Lady Moyong?

Is this half-sword double swordsmanship okay?

These guys were just like that without me. Why was he a friend I don't know? It's so awkward, like we won't even talk to each other.

The men get along well among themselves, but was it because they're women? Do women just have that certain feminine vibe?

I don't really know.

How would I know that in the first place?

It seemed like it would be a night when Qing's worries would deepen.

Dororong, squeak squeak.

Originally, Qing could sleep anywhere.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After spending four days in Taeju, it was time to eat breakfast and set off.

Hmm. I need to get these guys apart.

What should I do?

Now, after Soju, it's Hangzhou right away?

The face was shiny and bright, and the blue eyes were very bright.

This was what I think when I'm really excited about meeting my friends.

So, until now, I had never even thought about hanging out in the arena, but when the day came to leave Taeju, I suddenly thought of it.

After all, was this the fate of the strong?

What on earth could possibly go wrong with such fragile children?

So I guess I have no choice but to stay in Soju and sneak out?

So he departed from Taeju with his army.

Behind them, a swarm of onlookers followed, and the men who had thought they had given up on watching the fight now remembered their past occupations and left in large numbers. Instead, the blind followers of the Jade Kirin filled the place, and the gender ratio was reversed.

If I had to say, was it a gender reversal?

anyway.

If you follow the road east from Taeju, you will reach the city coast.

The march schedule was to arrive at the coast, then head south, cross the river to Hoeha, and practice crossing the river, before reaching Suzhou.

So, after staying at the coast for a day, they re-equipped and headed south, and then stopped at a small town called Yeogo-hyeon, along a tributary of the Hoeha River.

It was still an ambiguous time, somewhere between lunch and dinner, with the sun still shining brightly.

As soon as I thought, "Why, when we haven't even gone that far?", General Wang Ssangryong approached me and reported to me politely.

"From now on, there were no houses to stay in until we reach Namtong, so it would be best to stay here today."

There were people who were watching, but it looks like everyone was asking whether they should go or not while submitting a report.

I am serving my precious mother, but I also have a sincere desire to stay in a nice inn.

"Oh. Then let's do that."

But from Qing's perspective, there's no need for me to interfere with the march schedule.

And from the soldiers' perspective, it would be much better to camp next to the city and have some time to rest, so there's no reason to rush to meet a pretty girl anyway.

"But there were no houses along the way? Why? The road was so well-maintained."

"Sister, logistics will eventually spread out across the country, so even if there were official roads, wouldn't there be no one coming and going?"

"But isn't it strange that it doesn't exist at all?"

"Hmm. As far as I know, it's probably because the Japanese pirates appear so frequently."

"Japanese pirates?"

"They say they're Japanese, but true Dongyeong barbarians were rare. Rather, they're often bandits disguised as Japanese. Of course, they're rare compared to the general population, but isn't their tyranny so severe?"

"Hmm. What on earth does the military do? Ah. I'm not talking to you, General. This isn't even your territory to begin with."

"Hmph. Even Shandong Province isn't completely unscathed. The common people were so exhausted that they're even asking for help from the Hwangbo family."

This was the testimony of Peng Daesan, who lives in the village just above.

In an instant, Wang Ssangryong was drenched in sweat.

"Well, that's the thing. The Japanese know how fearsome the army is, and they're so elusive that even if we deploy our troops, they'll already have fled. So even if we deploy, it's futile…"

"Huh? So you didn't even go out?"

"That's it, that! Yes, rather, the army was exhausted and its fighting power was diminished, and this was due to disloyalty to the stern imperial family…"

Wang Ssangryong's sweat secretion becomes much smoother.

Sweats poured down his face like a waterfall.

"That's not the case. The director has devised his own countermeasures, placing the Cheonhoso villas along the coast. So, even during his time, the Japanese pirates couldn't dare invade. Well, if you ask the Shandong people, you'll hear that after that adjustment, the damage from the Japanese pirates has clearly decreased. And realistically, even we can't do anything about small-scale attacks of a dozen or so people…"

\textit{What the heck? I thought this guy is a talented general.}

Qing's eyes narrowed.

Wang Ssangryong could only gulped down.