\chapter{A Loner's Journey To Solitary Sword (2)}

\textit{No, isn't the orderly a subordinate of the general?}

\textit{Why are you reporting to me?}

It was a natural thing for the two orderlys.

How many days have they been marching together, and you don't know who's superior?

"Who was it?"

"They said that if I mentioned Namga and Unssi, you will know."

"…?"

Yang Sa-mok, seeing Qing's expression, felt as if he had already heard the answer.

"I will kick them out."

"No, don’t do that. Bring them here."

She didn't know who they were, but Qing doesn't turned away anyone who comes to see her.

If they asked to see someone, there must be a reason, so you can't just kick them out.

The two peopleo appeared like that.

"Hmm. You guys? When did you get here?"

"Young Lady Ximen…"

It was none other than Nan-Gong Shencai and Murong Zhuji.

Qing tilted her head.

\textit{Why were you using Namga and Unssi name?}

This was why pseudonyms were dangerous.

Even the person making it up didn't realize that it was their name, let alone a colleague's pseudonym, because after just a few days, they'd completely forget it and ask, 'What was your name?'

\textit{Hmm. Isn't there something wrong with them?}

\textit{I told them to go home, so why did they chase me again?}

\textit{But we made a fuss together.}

And then, since it was a problem, wasn't it Qing who stepped forward and said she would take care of everything by herself?

It'd be stranger that if she told them to go home, they just said 'Hehe, if you'l excuse me' and went home.

"I'm on my way back from escorting Lady Chen to the Wulin Alliance. The old man said he'd take her to the Divine Maiden Sect, so we're just hurrying to join you."

It was good news brought by an uninvited guest.

\textit{Yes, Changming is a baby, and the world is too dangerous for a baby who's only a First-Rate chick.}

\textit{At least until when you reach the Peak, you should go sightseeing with a guide. It's like a newborn baby left on the water's edge.}

If the world's best martial artists heard this, they would feel wronged.

However, it was said that during the time when Qing was first-class, she lived a life of self-sufficience, sitting steadfastly and cooking leftover food and harvesting crops.

But since I was a first-class person, I didn't get beaten up by beggars or chased by farmers, so I thought that Wulin was a world where the strong rule.

The monopoly of first-class, unmanned food—the exclusive right to unspoiled, premium leftovers! The freedom to roast rats and other things, openly emitting smoke and odor! And on top of that, the right to freely forage in the fields!

So Qing could say this with great confidence.

If you want to become a martial artist, you must at least reach the peak!

"Oh, Sister. Would you like to try some of this? This was called Cheonsudonpalgongsan Tofu."

"Huh? What was it? Soft tofu?"

"This was a delicacy made by boiling tofu and pork, stir-frying shrimp roe and bamboo shoots, and pouring chicken broth separately."

"Oh. Hmm. It’s okay. It’s mild and delicious."

"Sundubu, soft tofu. So, you're referring to this Ianjeomdan. It's a dish that's not pressed in a mold, so it has a uniquely soft texture, and it's also a dish that uses two layers of red sauce, a secret recipe from Hoe-eum."

"Oh! What was this? was this really soft tofu?"

"This was called Chwipijakdujang. It's sweetened, hardened tofu fried in a pan. It tastes even better when dipped in condensed milk."

"Hmm? It’s more like a snack than a dish."

Certainly, when Zhuge Lixian was by your side, the amount of information you receive was different.

It's delicious even if you don't know it, but it's even more delicious if you know it.

"This was called Seokma Tofu. For those who like tofu, this was the highest quality tofu, comparable to Joseon Tofu."

"Huh? Joseon tofu?"

"Ah. Do you know Joseon Tofu? Joseon was a barbarian country across the East Sea from the Shandong Peninsula. They make Joseon Tofu, the best tofu that tofu lovers would eat every meal of."

Qing blinked her eyes.

\textit{No, suddenly nation in a place like this?}

\textit{What, should I find the owner?}

\textit{But what's famous about tofu? Why tofu?}

\textit{Well, tofu from Zhongyuan doesn't taste like home.}

\textit{It's kind of runny, somewhere between tofu and soft tofu, bland or salty, and doesn't have much of a soybean flavor.}

\textit{But this Joseon isn't even my hometown, so what kind of nationalism was this?}

\textit{It's not like I came to the past, it's a parallel world, or a game, or something, so what the hell was Joseon?}

Qing just laughed it off.

\textit{I miss the cutting-edge spices and carbonation created by the best and brightest scholars in my hometown, but I don't really miss my hometown.}

\textit{Ah, thinking about it makes me want to drink some soda… }

But, why was it that all the things recommended were tofu?

Well, since a lot of salt was added to the brine for tofu, it was difficult to make it without using seawater.

So, all warm regions bordering the sea produced tofu as their specialty.

"Oh, by the way, Sister. Do you happen to be practicing any other external martial arts?"

"Huh? External? Specifically?"

At that, Zhuge Lixian's eyes sparkled.

In fact, Qing's martial arts that Zhuge Lixian saw was not that different from the usual, so it was impossible to imagine that she was secretly training her spleen muscles while eating and sleeping.

Then, it just meant innate strength.

The most excellent Tao in the world exists naturally without processing, and this was what Taoism calls non-action and naturalness.

This was the true power of nature!

"But aren't you incredibly strong? You lifted a two hundred and fifty-pound iron weight with one hand at the Clan's training ground, right?"

"Ah. That. I was a bit nervous about showing it to Xiang'er. Oh, and how were you, Xiang'er?"

Zhuge Lixian's eyes sparkled at that. As expected!

"Oh, that's ridiculous. She kept whining about wanting to see her Gege Sister every day, don't you think she's lovesick? Oh, that's right! On your way back from Hangzhou, would you like to stop by and see her face?"

"Oh. Is that so?"

"However-"

"It's Hoenam Beef Soup. A warrior should eat meat. How can a warrior exert himself by eating soybean scraps?"

It was a blunt voice that cut off Zhuge Lixian's words.

"Hmm? That's exactly what Chaolei said. And tofu was a complete food, right? Protein—well, I don't know about that, San, but for strength, white meat from chicken was better than beef, and tofu was even better."

"No, that's it? Was that the secret to your strength? White chicken, tofu, ah, that kind of secret—"

"Okay. Hoenam was an old word for Hoeeum. In other words, it's a noodle dish you can only find in this neighborhood, so eat it while you can."

Paengdaesan interrupted Zhuge Lixian again.

He didn't know why, but to Peng Daesan, this rambunctious kid has a strange, unsettling feeling, something different from before.

Look, even now, that guy who talked a lot but was always polite was giving me an impertinent look.

But Qing didn't think much of it.

Zhuge was a talkative person by nature, and San was a noisy person by nature, but he bought her food often.

Rather than that.

"What are you doing? Why are you following me?"

"…"

"What, am I talking nonsense?"

And then there was the child who would eat every single dish that Murong Zhuji reached out with her chopsticks.

"Oh, Lan-ah, then I can’t use it."

"But why was she here? Is she trying to sneak into our group?"

"She’s more suited to us than Changbin, who only has his name on the list, even though he’s not a regular."

Come to think of it, it's a bit much to say that they matched.

He said he just hugged his knees and dozed off to white noise, so if I had to say, should I say he didn't even do the tour?

As Murong Zhuji's face turned sad, Qing changed his words.

"But if you only consider the participation rate, it's higher, right? Then you'd be an honorary member."

"Young Lady…!"

"No way. Whatever you want. I can't accept it."

"Then shall we take votes? Alright, members of the Half-Sword Double-Saber Society, those in favor of Young Lady Murong being admitted to the group, raise your hands!"

Four hands, including Qing, raised up, and Tang Lan-ah snorted with displeasure.

So, Murong Zhuji suddenly joined the Half-Sword Double-Saber Society.

Meanwhile, the general trembled.

\textit{How far does Madam's relationship extend!}

\textit{Look at the faces of the young people gathered here.}

\textit{Nan-gong! Peng! Murong! Zhuge! Tang!}

\textit{Since all the children of the Five Great Wulin Families have gathered together, isn't this a true friendship that came to help in the most difficult times?}

\textit{Of course, their intentions were obvious.}

\textit{Although it was said that government affairs were inviolable, even if the two do not invade, they do help.}

\textit{This was the harmony between the administration of the country and the local aristocrats and the real ruling power, as they look at each other and help each other out, for your good and for my good.}

\textit{When you reached the top five, you were usually a powerful family, so you rarely bowed down to the officials like a quasi-governor. But isn't Madam worthy of being called a quasi-governor?}

\textit{So even the arrogant and proud members of the Five Great Families have no choice but to gather together and call themselves close friends.}

The general's loyalty grew stronger and stronger.

His loyalty that had been shrinking little by little whenever Qing'er ate recklessly and gently stroked her swollen belly or whenever she immediately showed her disposition, rose again like a kite in a strong wind and reached the sky.

Of course, we still don't know what the outcome of the General's dedication will be.

Since he grabbed the longest and strongest rope, he might just fly higher.

Or maybe it's too close to the sun and was destined to burn up.

So, after the noisy banquet ended, the general quietly asked,

"That, Madam?"

"Yes?"

"I know this may be presumptuous of me to ask, but I wonder if there were any membership requirements for that organization called the Half-Sword Double-Saber Society…"

"Huh."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The group, having eaten well and had fun, heads to the next city.

Taizhou!

This city, located in the heart of Jiangsu Province, has a surprisingly unspectacular history.

Despite its existence spanning over two thousand years, there were no notable people here, and no significant footprints have been left in Jungwonsa Temple.

If you had to pick one, you would say that there were a lot of wonderful caves?

And Qing, um.

The fate of life and death has now been completely decided.

It's ruined.

The arena's canopy now resembles a giant, mobile pavilion.

Wouldn't it be true that the entire direct line of the Five Great Clans were occupying the seats?

No matter how great the resentment of losing one's father, teacher, and friend, one has no desire to commit suicide by jumping into that fiery pit that burns with a spicy, hellish flavor.

Because grudges only have meaning if you succesfully took revenge.

This was one of the few advantages of being a Zhongyuan person.

At least the people of Zhongyuan do not let their resentment lead to self-destruction, so they swallow their resentment and try to resolve it somehow, and when things were unfavorable, they know how to retreat and wait for the future.

Even though this resentment was hotter than that of any other nation, it has the rationality to compensate for it with greater joy and gain!

So, Qing wanted to separate from her friends.

\textit{The life-or-death decision was just something I did to reach the Unrestrained Realm, and since I asked for the General's cooperation, it wasn't really that dangerous.}

\textit{But because of these guys, life and death were ruined.}

\textit{I also had the intention of settling some of the grudges, but who knows what those really crazy guys will do?}

So, Qing's heart was uneasy.

\textit{Hmm. Would it be better if I go to Shuzou and then head to Hangzhou alone?}

\textit{But they'll chase after me soon, right?}

\textit{Since Yuanying didn't tell me the time, if I go and come back in the middle of the night, then since I sleep with Lan-ah and Miss Mo-yong at night, I can't help but know…}

\textit{But, instead of reducing the numbers? Why?}

When she woke up, for some reason, there was one more person.

"Miss Ximen. It’s been a while."

A faint smile like a wildflower.

A faint presence that didn't stood out no matter where it is. To put it nicely, you could say it's comfortable and plain, but anyway.

Suddenly, she had an auditory hallucination that sounded like a small dog breed like a Chihuahua growling.

"Shh, Lan-ah. You can't use it. Young Lady Gongsun? What were you doing here?"

Then Gong Sun-Yaoyi grabbed Qing's hand.

"I heard Young Lady Ximen was going through a major crisis. As a friend, I thought I should help. My family home was in Nanjing, so it's right around the corner."

"Uh, um. Thanks. But it could be dangerous."

"I, too, have been working hard to catch up with Young Lady Ximen. I recently had an epiphany, so I'm sure it's the will of the Heavens to help Lady Ximen. Even if that's not the case, I really want to be of help."

This was one of the reasons why the elders of the Wulin Alliance liked and liked Qing.

A close friend who stimulates the pride of the martial artist was both a soft whip and a tasty carrot that leads the post-Jeongpa index members to training and raise their level.

Of course, the biggest factor was the sharpness of Elder Slayer.

Anyway.

Gong Sun-Yaoyi's smile may be delicate, but her kindness was so radiant that it radiates like rays of light.

So what can Qing, who was weak to kindness, do?

"Oh, that’s it. Um, did you eat breakfast?"