\chapter{A Loner's Journey To Solitary Sword (7)}

But, um. I don't get it.

Even though she may seem thoughtless, she was actually a cunning woman who measures each point more closely than anyone else.

It was even more vicious than the former in that it was more concerned with the angle of exit than the angle of entry, and if that didn't work out, whether it could escape or not.

Anyway, you just have to figure out how to make a gap to get in.

The secret to a surprise attack was to strike first. What's so difficult about breaking in with just one blow?

This vicious pseudo-Chinese person has no regard for basic human qualities such as pretext and face, which should naturally be taken care of!

But why? Samurai? was that right? were there samurai in this day and age? was that what they're called in this world? They're a bit out of place for a samurai, but what kind of samurai were they? They're just a bunch of short, primitive men. What the heck, I'm coming to my senses. Give me back my samurai.

You need to know your opponent even a little bit to decide whether to stab them or not, but since you have no idea whether they were strong or weak, even if you were a master of assault, Hmm. This was a bit much.

"I'll give you half an hour! We'll attack immediately when the sun was halfway up, so open the gates obediently, welcome Miju and the young beauty, and offer them the goods from the warehouse!"

The ability to tell time by looking at the sun was a basic skill of people in this era, an ability that was acquired instinctively through data accumulated over the years of life.

The expression "half-set" was used because the sun would be above the horizon at about half an hour.

Then, the Japanese pirate's lackey seemed to be talking to the Japanese pirates, and then he came forward again and coughed.

"I will correct this. This angle. This angle. I will give you this angle. This was the only angle I have extended out of mercy, so please don't shed blood in vain and surrender quickly!"

Qing was speechless.

This angle was thirty minutes in the blue system.

Where in the world were there people who declare war and then give this much?

Isn't it a tight schedule for the decision makers to gather for a meeting?

If the Qing were well-versed in history, they would have found it surprising that they declared war on the Japanese.

Because the human intelligence cannot understand the concept of declaring war.

What the heck was a declaration of war? You have to declare you're going to attack before you attack? Why should we?

Ah, I see. So you're saying, cut off one limb first, and if you don't want more to be cut off, surrender?

Qing was a bit suspicious of that confidence.

If you don't surrender, you'll all die. This isn't something you'd say without a strong conviction.

But there's a wall? What the heck?

While Qing was observing the Japanese, he was wondering what level they were at as martial artists.

Only then did the general, who had come running in a hurry, gasp for breath and sprint to the side.

"Ugh, you, you, damn Japanese, ugh, you little bastards, how dare you!"

"Ah, General."

"Ugh, whoa, those bastards, whoa, I'll shoot them with my arrows right now."

"We shouldn't chase them away, we should get rid of them."

"Hmm. You mean annihilation? Hmm. That's it. Hmm."

Then Wang Ssangryong suddenly came to his senses.

It's Mama's order, what the hell were you talking about!?

"No! Huh! That's right! How could we allow those ruthless Japanese to trample on the Emperor's land! My Lord Wang Ssangryong—"

"Just a moment."

Qing notices the sullenness in Wang Ssangryong's words and tries to stop the general.

"Are they strong?"

"No! Five of our elite warriors from the Shandong Army can easily take on one enemy. We may be somewhat inferior, but we can overcome them with our mental fortitude. Yes!"

"Five was one?"

This does not mean that one soldier can fight five Japanese.

It was Wang Ssangryong who was very proud of the fact that five soldiers could fight one Japanese.

No, what the hell were you bragging about?

But judging by your attitude, it must mean that you have something to brag about.

"Unless you're an elite warrior? How many do you need to fight one Japanese?"

"Well. If those inexperienced, weak soldiers from Honam were to face one of those twenty, I think they'd have a hard time. That city commander there was quite the weakling."

For reference, the Honam Provincial Commander was Wang Ssangryong's long-time nemesis, and they were snarling at each other, seeing each other as thorns in each other's side.

Elevate yourself and humble your enemies.

Wang Ssang-ryong was someone who has the basic political stance ingrained in him.

Anyway.

Wang Ssangryong's answer was as follows.

If you have a thousand two hundred soldiers, you can easily drive them out by shooting arrows along the wall.

But the destruction will be accompanied by much bloodshed, and of course, our Shandong Army was prepared to fight without fear and die.

He thinks of the Qing soldiers.

Shouldn't the military come out and destroy those barbarian raiders?

But was that right?

The faces of the soldiers who called the fairy with various but respectful titles such as "Shinnyeo" and "Mama" and shyly offered snacks and wild flowers.

The soldiers of this era were those who were brought in to pay military service instead of paying taxes.

So, was there any justifiable reason for them to shed blood? Aren't they professional soldiers, prepared for battle, ready to risk their lives and receive a salary?

Should we force them to shed blood?

What did I say?

It would be the same no matter what I become.

But what if you shoot an arrow and chase it away?

Would those who made necklaces out of human parts suddenly become frightened and gentle, and quietly back away, saying, "Let's go home, you bastard?"

It's obvious that once the military leaves, they'll come rushing back.

If I had my way, I would just jump in and slaughter them all.

What if I jump in? What about my friends?

It's obvious that these weaklings, not knowing the subject, will jump in and say something nonsense about protecting us, but um.

Ha, I really feel more comfortable being alone.

It was the thought of the person who was buried among his friends, his face brightest and most excited.

If someone listens to her true feelings, she'll say that she's full because she whines about missing her friends.

"How about me…"

Qing's eyes waver.

What should I do?

But, the soldiers, how could they drive us to death while we were still close? What on earth could I possibly say, and by what right did I have?

But why let me go? Knowing full well what I'd do if I let you go? That's not right. It's not right. And that's why it's not right.

If you didn't know, you wouldn't know, and even if you did, you wouldn't pretend not to know. That would be cowardly and unjust.

If I step out, what about my friends?

Roughly speaking, twelve and a half soldiers were fighting one of those vicious Japanese. If the kids rush in because of me and get hurt, I'll be fine.

Is this something I should be deciding in the first place?

But, I can't just stand by and watch.

But I couldn't just worry about it, because this moment was so short that it passed in the blink of an eye.

So, Qing finally gulps and opens his mouth with difficulty.

A white flag flutters above the gate.

Jang Seok, a traitor who changed from a common slave to a guide for the enemy, smiles cruelly.

By the way, the official name for these guys was Han-gan, which was a serious insult and swear word meaning traitor or collaborator with foreign powers.

Of course, Jang Seok also has something to say.

All those Zhongyuan people gave me was beatings, rotten food that even a dog wouldn't eat, and the harsh labor wages in the salt fields. Isn't that ridiculous?

"Hi, Shogun. (The following was an interpretation.) The lambs say they will serve the general."

"It's a shame. It's more fun to rebel."

"Even those bastards know their place. They say that if you don't offend the gods, they won't bring disaster."

"So, does that make me a god? Hehe. What, these lambs of Zhongyuan don't know bravery? Come on, you guys! It's been a while since I've soaked myself in blood!"

Of course, I have no intention of just accepting the woman and tribute and quietly disappearing.

Because if you want to return to Shinto and show off your bravery, you need more noses, proof of your conquest.

The proof was that they will soon return with loyalty, so aren't Zhongyuan guys excellent beasts who have nowhere to throw away?

So, as the Japanese pirates marched towards the castle gate, the gate opened with a creaking welcome as they got closer.

Then, three carts appear right away.

It was covered with a tarpaulin so its contents cannot be seen, but it looks like something convex was sticking out.

The general tilted his head, his bright crown gleaming in the desperate sunlight before falling.

"What? Korewa."

Qing's amazing hearing and verbal skills allow him to hear the general's words.

What was this?

Qing bursts out laughing.

What the heck, a cannon.

Come to think of it, I wonder if it's really necessary for people to go out and fight in such a dangerous way.

If you have good tools, of course you have to use them, right?

Kkwarung!

A loud noise like lightning striking right in front of your nose!

Crumbs of stone fall from the walls, and the gate I stand on trembles and tickles the soles of my feet.

It was a truly earth-shaking roar.

Three cannons loaded with iron rings.

Qing sees the magnificent destruction.

A fiercely fragmented piece of metal pierced through the human skin, then emerged, and, even at a speed that had lost momentum, it managed to embed itself in another body and disappear without a trace.

A bold straight line, the fastest thrust, branches out into tens of thousands of branches.

It's not powerful enough to pierce two people, but that's because of the irregular shape of the projectile, not because it's lacking in power.

Well, how do you stop that?

It was Qing who realized the power of the cannon once again.

If you get hit from a distance, that is, gently, you can somehow withstand it with self-defense.

What if it hits you up close? Hmm.

When the cannon was aimed at you, you should just run without delay.

Looking down from the castle gate, the middle was completely cut off, like a Japanese man's unique hairstyle.

The only ones left were the Japanese who had been lucky enough to spread out to the left and right, and even they were left speechless by the tragedy.

Some people just stand there with their eyes wide open, some people sit there not knowing what to do, and some people even urinate themselves.

That was after my colleague was torn to pieces and scattered in an instant, with a deafening roar, so that even his body could not be found.

Because there was not a single intact corpse left, only a fan-shaped pile of red mud remained.

Qing flies out of the castle walls.

The anti-gravity walking of the Moon Lady was not a martial art that actually resists gravity, but rather an illusion that gives the illusion of falling slowly with elegance.

Of course, anyone who sees a beauty landing gracefully will feel as if time passes slowly.

Qing kicks the Japanese pirates.

It may look like a thud to others, but to the Japanese who were being hit, it was a very iron leg with bones that break and crack with each blow.

"Run away!"

I wish I could see some of that samurai's skills, but he's turning his back?

In fact, just like those thieves, once the price was broken, they just end up being a collection of individuals with flawed character.

It's a pity, but on the other hand, it's a reaction that feels fortunate.

Because, as expected, there were burdens that follow them around, so they will just sit back and watch on the weak subject.

Even though they were weak members of the Half-Geom Ssangdohoe, it wouldn't be too dangerous to chase down those who have lost their will to fight and were running away.

In the midst of all this, Qing glances at her friends.

Is everyone okay? was there any danger?

Thanks to that, the blade was stuck right in front of my nose.

Of course, just because you open your eyes doesn't mean you have a blind spot.

As I raised my hand to block, the famous sword hit my wrist and broke with a loud crash.

In fact, although the blade was sharp, it was also notorious for breaking easily.

If you don't cut it, it will break and shatter right away, so it was a perfect match for the strong arms of the minority magician who has reached the level of the indestructible diamond of the Qing Dynasty.

However, if you try to block it, you can roughly guess its power.

This was quite sharp, but if it's not a self-defense weapon, if it hits below the peak, it'll be completely cut off.

So, Qing once again strengthens his resolve in his heart.

This can't go on like this.

I have to get rid of them all and go alone.

Well, even if you leave out the weaknesses, you shouldn't involve your friends in personal matters.

Because I have to take care of my own business,

Do your own work. Do it yourself. Why, that's right.

All by myself, for myself. Only by myself.
