\chapter{A Loner's Journey To Solitary Sword (11)}

On the third day in Soju, it was a busy morning, usually with preparations to tear down the military tents and move the base.

But the soldiers were extremely relaxed.

"Oh, Cheonho, please have breakfast."

"Uh, uh, breakfast, what's breakfast…?"

"Fried dried pollack, stir-fried zucchini, garlic, and eggplant, and Donghae soup-"

Fried dried fish was roughly fried dried freshwater fish, stir-fried pumpkin, garlic stems, and eggplant was roughly fried with oil like stir-fried vegetables, and Donghae-tang was a derogatory term for soup that has as much water as the East Sea but no ingredients.

"Get rid of it. Ugh, you're not just chasing away my appetite, you're just beating me to death. I'm better than you. You eat a lot."

It's a miserable diet from the morning onwards.

But the fact that military food was miserable was a common characteristic of all cultures.

It's not military contempt.

There were many ways to take bribes by skipping out, and it was a common phenomenon even in non-military groups without professional cooking facilities or cooks.

"We'll have lunch on the road today!" Why were the soldiers, who must set out with such solemnity, so spread out so early in the morning?

Well, I decided to stay one more day.

Why? The priestess wants to see the stone.

So, that means you delayed it by a day to go sightseeing.

But far from being dissatisfied with it, the soldiers nodded and responded that it was natural.

Of course, if you've come to Soju, you should definitely check out the Hogu. You've only been training in the arena so far, so how could you not take a look around this wonderful Jiangnan area?

So, sucker!

The correct name was Hogusan.

But it was just a gently rising hillside, only ten zhang high at the top, about the same height as a ten-story building in Qing's hometown.

It was embarrassing to call these hills mountains, so they were simply called Hogu, and they were the best tourist attractions in the land of Soju.

This small hillside was packed with so much to see, it's a truly tourist-friendly destination.

First, there was a tower at the top.

Su Dongpo, the poet of Zhongyuan, left behind a passage that said, "There was nothing more regrettable than coming to Suzhou and not seeing the Hukou Pagoda."

The Hogu Pagoda was a seven-story Buddhist pagoda, a gigantic structure that was sixteen jang high and half the height of Hogu Mountain, which was ten jang high.

If there was a characteristic, it was that it was tilted crookedly.

"Oh, this. I know it. The Leaning Tower, the Leaning Tower."

Even in the hometown of Qing, it was called the pagoda of Zhongyuan.

Of course, Hogutap will be wronged.

Because the Hugu Pagoda was built two hundred years earlier, wouldn't it be logical for the pagoda to be the Hugu Pagoda of the Western Regions?

Why would the Hogu Tower, a two hundred year old building, be used as the pagoda of Zhongyuan?

However, it was a claim that no one seriously supported, even among the people of Zhongyuan, as it was only a joke, probably because it was inferior in slope and height to the Satsap.

If you feel wronged, you can tilt it even more.

"Sister, do you see the pond below? This was the pond where King Heopryeo of the Wu Kingdom (not that Wu Kingdom) was said to have thrown away his three thousand swords. However, since none of them have actually been discovered, it's likely nothing more than an exaggeration in historical records. But aren't you curious about how such a story came about? People say the pond resembles a sword. Oh, you can't tell from this angle, but from below, it's long and straight—"

"You really talk too much. Hmm. Eat this."

Interrupting Zhuge Lee-hyeon's words, Paengdae Mountain holds out a beautiful, pink, translucent rice cake.

"No!? Where did you get such a precious snack?"

"I picked it up on the way."

Qing pretends to narrow her eyes at him.

Of course, there was a smile on his lips.

Qing doesn't know the destructive power of my face.

The sight was truly beautiful, and the mischievous smile was so charming.

At that, Paengdaesan's eyebrows twitched.

"Don't smile so casually."

"What? Why?"

"……You're so ugly, you deserve to get hit."

"Did you say it was annoying?"

"Hmm."

"No, but where do you keep picking them up? I need to know something. There seems to be a place where they're all dumped. Now's the time to just pick them all up and bury them."

Peng Daesan coughs and turns his head away.

But Qing, who doesn't know the circumstances, was pleased.

No, has our San-i changed?

Can't you see my mouth was empty these days?

It's Peng Daesan who has been nagging me for a long time, but he has always bought me food and snacks.

But it's different from before.

The guy who pretended not to be able to resist buying it even though I begged him to buy it for me?

Now, like grandmothers who were anxious because they can't feed their grandchildren, they will keep offering snacks.

And yet, with their mouths, they say things like, "Eat this," "Eat this and shut your mouth," "Don't waste your energy and eat this," etc.

If you ask where they got it, they say they picked it up somewhere, someone gave it to them, or they sold it to a peddler because they felt bad for him because he couldn't do business.

What, spring potatoes were delicious?

Are you trying to act cute on the topic?

But the rice cake was delicious.

If it's pink, it seems like it should have honey or sugar in it, but the part where it's just plain rice cake without any filling was annoying and deceptive, and the texture that's close to a rice cake with oil applied to make it chewy was also annoying. The subtle sweetness was really annoying.

This was so annoying, I can't do it.

Samjin was annoying. I need to chew him up and scold him.

As Qing was chewing the rice cake, Tang Lan-Ah suddenly jumped up and blocked Qing's path.

"This again. Qing'er, I'm hungry too."

"Huh? You just came up after lunch? Already? I'm still full, but you're already hungry? Didn't you eat a lot earlier?"

At that, Tang Lan-ah's eyebrows twitched.

Well, that's what I'm saying.

No matter how much you say it, it's something you absolutely don't want to hear.

Isn't that too presumptuous of a thing to hear from a girl who eats ten times as much as other people and then swallows the snacks that that weasel-like bastard gives her without any hesitation?

"Uh, I don't know. Uh-"

"No, all of that, what was it, if there's not enough sheep, then they say there's not enough."

He was a child who ate all the leftover rice cakes and some nameless, disgusting snack in one bite.

Seeing that, Qing thought, "Hmm, you must have been really hungry. Then let's eat more lunch."

"Look, my lady. The carp was as big as my arm."

"Oh, really? Wow, really big. It'll be delicious if you boil it well. The bones were a bit bothersome, but still, carp soup… um, carp soup was good."

"……?"

"……?"

"Oh, Sister! Do you see that pavilion over there? That pavilion was none other than Sun Wujing! It's the very training ground where Sun Tzu, the author of The Art of War, trained the soldiers of Wu!"

"That grandson? Really? Really?"

"That's right! The reason the Wu nation was able to stand tall as the dominant power of its time was not due to the abilities of He Liu, but to the two favorites, the renowned prime minister Wu Zixu, and the great general Sun Tzu. This, in turn, stemmed from the loyal officials who had been well-versed in the rise and fall of nations: Guan Zhong of Qi, Xian Zhen of Jin, Sun Shuao of Chu, Fan Li of Yue, Bai Li Hai of Jin, and—"

"They sell it over there. Eat this."

"Hey, San? What's this? You want me to eat it? Hey, San, why were you suddenly so curious?"

"Huh. I don't remember ever being disappointed with food."

"Yeah, that's true. Hehe, I'll eat well."

Anyway, the Hogusan tour was fun.

With this number of people, it would be fun to just walk along the road even without going to Hogusan, but it was worth it to force myself to extend the schedule by one day.

And finally, the test stone!

Qing thought that if he just went out for a day to play, he would probably meet a suspicious friend.

Then, Zhuge Lixian's miscellaneous knowledge of all things, if left alone, would be an endless chatter that would last for a day, two days, ten days without a care in the world.

Come to think of it, why was Zhuge getting so talkative? He wasn't like this before, but now he's following me around and commenting on things.

- I found a good selection inside.

That was the test stone.

As the name suggests, the test stone was a stone used to test swords.

This was the place where the most famous weapon of Zhongyuan, the legendary sword, and not just one, but two swords, the Ganjang and Makya, were tested.

King Hapryeo of the Ona Kingdom was said to have collected three thousand swords.

As his desire for swords was the greatest in the world, he summoned a craftsman named Ganjang and instructed him to create the best sword using the best materials.

Soy sauce was made by learning ironwork from Guyaja, the best swordsmith of the time, so he thought you could make it too.

Soy sauce created a sword.

In the process, he had the help of his wife, Makya. Depending on the neighborhood, there were stories that Makya's hair was put in, and there were even stories that Makya threw herself into the furnace like Emile Jong.

Thus, two swords were born.

It was the moment when the legendary swords, Ganjang and Makya, were completed, a pair of swords named after him and his wife.

However, Ganjang offered only the wife's sword, Makyaman, to Hapryeo.

Because I sensed my end.

So, King Hapryeo of Oh, who had received the Makya, was so impressed by the cool blade that he struck it against a rock.

Then the rock was cut cleanly, and the sword was left without even the slightest scratch, so it was truly worthy of being called a legendary sword.

This cut rock was the test stone.

So, it wasn't that strange of an excuse for Qing to ask to see the stone.

What's so strange about the prosecutor seeing the marks of the sword?

Since he was a young man who could read the precepts of the cliff, he brought all his friends together, saying that he might gain some enlightenment and that they should hold hands and climb over the wall.

Qing and finally see the traces.

Then, Gong Sun-Yaoyi spoke carefully, but with curiosity.

"Miss Ximen? What do you think? Is there any images or feelings…?"

"Huh? It's just a stone?"

Of course, it's just a stone.

What the hell was a test stone? Isn't it just a split stone?

"That stone? Sword Friend! Can't you see this sharp cutting edge here!? As expected, Makya, they say there were countless treasured swords in the world, but the best of them all were a pair: Ganjang and Makya. Look at this unfading artifact, even after countless years! Ah, if only I could see it just once, I would have no more wishes! Since Geomwoo has set his sights on the Yang Sword, I thought that Heaven would surely open a path for him to reach the two divine swords, but this sword fight was truly, truly moving!"

Nan-Gong Shencai was making a fuss.

But to Qing, it just looks like a broken stone.

Of course, it was impossible for primitive people two thousand years ago to have made a famous sword that cuts stones with their primitive technology.

Even if it were a truly famous sword, it would be the same.

The first martial arts sword of Zhongyuan, the Moon Sword, came from the era of King Fuchai, son of King He Lu of Wu.

So, since it was a time when the concept of martial arts did not even exist in the still underdeveloped Zhongyuan, how could there be any visible marks even if they were real sword marks?

So, it was Qing who realized that the inspection stone was just a trick to attract tourists.

Instead, I understood very well why the Onara was destroyed.

King Oh-Wang Heo-Ryeo, who had obtained the Mak-Ye, thought, "If I keep this craftsman alive, he might be able to make another sword like this!"

Originally, the best sword was only the best because there was only one of it, but once there were multiple swords, it could no longer be called the best.

So I have to kill this craftsman.

It was a truly disgusting way of thinking, and since no one could stop the king, he did it.

And what was it like when he died?

There was a pond called Geomji who threw away the swords because he said that he would take the three thousand swords he had collected with him to the afterlife and bury them together.

Even the best bastard in the world doesn't have a bastard like this.

And across the index finger, there was a large square with red stones scattered about, called Cheoninseok.

After Hapryo died, Hapryo's son, Bucha, built a tomb for his father on Hogusan Mountain.

However, Bucha, who was worried that his father's tomb might be robbed, made every effort to keep the location of the tomb from being discovered.

After the construction was finished, he held a banquet to thank all the workers for their hard work, then killed them all.

So the banquet hall was completely covered in blood, and the reason the stone statue was red was because the blood from the workers' resentment was not draining.

According to some records, the number of laborers reached 100,000, but anyone who looks at it thinks that's a bit too much.

In any case, he was a traitor who, in the name of protecting the body of his already dead father, instead of rewarding the people he had treated harshly, he killed them all and silenced their mouths.

The son of a son of a bitch was also a son of a bitch.

The previous king's son of a bitch, the current king's son of a bitch.

Of course, the country had no choice but to perish.

According to legend, this was the reason why the Nine Heavenly Women came to the country of Wol to teach its soldiers.

It was the will of heaven to destroy the country ruled by that son of a bitch.

On the first night of Soju, Lan-ah and Iri.

On the second night, Lady Ye and Mo Yong.

And on the third night, it was Qing who went to bed with Lan-ah again.

But, Lan-ah, this kid just won't fall asleep.

After a while, the hand that had been fidgeting curled up and he let out a deep breath, thinking he had fallen asleep, but why was he so bright-eyed?

If Qing makes a sound, wouldn't he wake up like a ghost and ask, "Hey, Qing? Why were you going to the side?"

Compared to that, Gong Sun-Yaoyi and Murong Zhuxi would come out and hug each other well if you put them together, and when they were entangled together, they would sleep soundly, dreamland, long-term business trips, and faint.

So, just like this.

I see Qing slipping out of bed like a snake, and the two of them embracing each other affectionately and smiling softly.

A faint smile appears on Qing's face.

And so, at night, Qing, carefully dressed, disappeared silently from the inn.

A journey that Baek-i took alone, as he lamented in the past.

Because only by lonesome you can achieve the Solitary Sword.\footnote{Another possible meaning of the chapter's title}