\chapter{A Loner's Journey To Solitary Sword (3)}

If you had to pick one word that Hangzhou people hate the most, what would it be?

It's Jiangnan.

Because Jiangnan was a term that refers to Hangzhou, Suzhou, and the surrounding area.

However, Jiangnan's reputation comes entirely from Hangzhou.

The rest of the soju and others claim that they created the extremely evil word Jiangnan to try to get into the hanger-on by adding to the reputation of Hangzhou.

So, Hangzhou people can't help but hate the word 'Jiangnan'.

That makes sense-

The best entertainment district in the world and on earth.

This was something that all the people of Zhongyuan acknowledge.

The most beautiful city in the world.

This was a strict evaluation from the perspective of a Westerner by Magapara, a Westerner official who worked in the government office about four hundred years ago.

In the Qing homeland, this Westerner, Magapara, was called by the twisted name of Marco Polo.

Anyway, Hangzhou's beauty was the best in the world.

It was a self-evident truth that both Eastern and Western civilizations agree on!

Is it just beautiful?

no.

Hangzhou has a population of a whopping 1.3 million, making it one of the largest cities in Zhongyuan.

So, even if about 15 people disappear every day, it was completely natural and no one would suspect anything.

As people flocked there, there were tens of thousands of beggars on the streets, so there were many who didn't care if they disappeared.

Hangzhou was also the largest gambling city in Zhongyuan, so there must be hundreds of people out on the streets every day.

There was a population of 1.3 million, but the central government's administration was not up to par, so even if someone disappears, that's all.

Who's missing? What, a civilian?

You bastard! If you try to solve every little thing like that, you'll be short of work even without sleep. How can you possibly run the country then?

So, even if someone disappears, you have to find them yourself.

What, Mr. Kim? Oh, I knew that kid from the time he started hanging around the casinos, running away in the middle of the night.

What, Mr. Kim? What's your name? Hey, what was the name of the Mr. Kim we caught and sold last time? Oh, thankfully not. Even if we're the last of the human race, wouldn't it be a bit much to sell out a friend of a friend of a family member?

So where was that Kim?

"Gasp, gasp, gasp!"

"Ah, sir……!"

Surprisingly, somewhere deep underground in Hangzhou, they were having a quarrel.

"Ugh!"

"iced coffee……!"

As Kim's body trembles, the eyes of the woman lying below flash ominously.

Originally, Bangjungsul was a Taoist technique that circulated each other's energy through intercourse to create mutual prosperity.

Some evildoers realized that monopolization was more effective than coexistence, and so they developed the practice of monopolizing sexual relations and stealing the essence.

However, Kim's penis did not go out and turned towards the sky again, so the woman's method was not a sorcery to steal and steal affection.

Rather, it was the original art of Taoism, where energy circulates with each other, nurturing each other's desires, and thus, one enjoys it endlessly without getting tired.

A time of such passionate passion passes.

How long has it been?

As Kim rolls over, panting, he pulls the woman's head into his arms and expresses his satisfied affection.

Then, the woman's hand gently caresses Kim's forehead, her heart.

The woman's fingertips circled, then at one point slowly lowered to caress her plump upper abdomen, and at another moment, they shot into the leather.

"Ugh, it tickles, stop, ahh."

Kim's laughter becomes a choking scream and echoes through the underground stone chamber.

Well, if you get your hand stuck in your stomach while you're alive, anyone would scream.

Mr. Kim causes a ruckus by pushing and hitting the woman.

But the woman didn't even pretend to be in pain; she just dug into her intestines, feeling around until she finally grabbed her heart, which was pounding so hard it felt like it was going to burst.

Then, he carefully cuts open the blood vessels with his long nails, and after a while, a whole heart comes out in his hand.

"Turn off……"

The woman who took out the heart glanced at Kim, who was foaming at the mouth, with an indifferent look, and then quickly walked out the iron gate.

There were numerous iron doors lining the hallway, and various scenes flash through the half-span-sized windows.

A scene of torture where a man and a woman were stuck together, their chins were fixed and they were forced to eat porridge. The person with their limbs cut off must have been a warrior, judging by their martial arts attire.

After passing through such a long corridor, at some point the floor becomes white jade and covered with red fabric, and at the end of it, a grand door appears, as magnificent as a palace.

"My disciple Yeon-ryul invites Mahi."

-Come in.

The woman opened the door and went inside, and there was a woman sitting on a throne in front of a huge tent embroidered with a phoenix.

It was a sight that would make anyone in Zhongyuan think they have gone crazy.

Are those crazy traitors setting up an underground palace?

This was entirely to the taste of the Siksim Demon Army.

Just by looking at the way he forces his followers to call him the Demon King of the Blood Cult, you can tell that he was a very corrupt person.

The Blood Cultists were also terrified, but there were more than one or two madmen in the Blood Cult.

He's a madman who calls himself a king. In fact, you could probably call him pretty crazy.

But if you don't praise it in front of others, then I would say you were very sensible and crazy.

Anyway, that's why the Demon King.

And the Demon King's daughter? Mahi!

The flow rate of the Seopsimmahee.

Yuryang, holding the heart on a tray, picks it up in his hand, examines it, and soon smiles with satisfaction.

"Okay. It’s a product. Gulp."

Then he takes a bite, grabs it with both hands, and rips out the tough heart.

It was a very greedy and barbaric sight that could be seen with the naked eye.

If someone saw this, it would be a truly pathetic table manners. It would be a miserable sight that would make them click their tongue and ask, "Aren't there any adults in that rascal's house?"

But I don't care about the flow rate.

Courtesy was something the weak show to the strong, and for Liu Yang, whose father was the Demon King, it was a virtue he didn't need to keep from the beginning.

The woman swallows hard and looks at her meal.

The look in his eyes was so earnest that it seems like he's sending out a message of desire, "Please give me just one bite."

He chuckled and took the last big piece with his finger.

A woman jumps towards the heart flying in a parabolic arc and catches it with her mouth.

"Oh, right. There's that guy, right? Heavenly Blossom Sword. I heard that the Five Great Kings have three children attached to him right now? And that Jade Kirin was one of them too."

"Hyeon-a-ae-il-mian, gulp, were you talking about the world’s most handsome man, Ok Gi-rin?"

"Yeah. That jade giraffe. How handsome does he have to be to cause such a stir? Aren't you curious?"

"The girl was curious too."

"Well, it's not like he can compare to our Lord. You know what? If we pull off this grand plan, he'll even consider getting married. Gosh. I'm getting married?"

He sits on a large throne, legs flailing, and lets out a cheer that sounds like a scream.

Except for the fact that her lower body was covered in blood from having her heart eaten out, she could be considered a girl who was properly in love.

"Congratulations, Ma’am."

"Yeah. Yeah. I didn’t know I would benefit from your help."

The woman had to wonder for a moment who her older sister was.

Well, until recently, she was called a bitch who smells like a rotting corpse, or that unpleasant bitch, etc.

Then, suddenly, she was promoted to older sister, so it's understandable that she didn't understand.

Seopsimmahee and Yuryang smile brightly, but with a somewhat malicious smile, they ask for advice.

"My marriage is at stake. So, don't make mistakes and do your best. You don't want your heart ripped out."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

With the addition of Gong Sun-Yaoyi, the entire Half-Sword Double Sword Society has gathered together.

Changbin was originally a bad member with a terrible participation rate that only put his name on the list.

\textit{I wonder perhaps because there were always women in the front yard of Mucheon-gak, I could understand with Changbin's circumstances of avoiding women. Does that guy think women will eat him or something?}

\textit{I'll have to throw him away later in a place where only female members gather.}

So, after a simple breakfast, Qing took the lead and left the Daejujeilgaekjan Shinsungeoru.

However?

-Oh my, listen, please get out of here. A noble person was staying here. Oh my, you can even pay your respects?

-Answer me, no, if you don't want food or money, then at least tell me what you want. What were you trying to do in front of someone else's store?

-Are you listening? Oh, you're making me going crazy.

From outside the inn, you can hear someone, presumably a server, making a loud noise.

"Huh? What’s going on?"

Then Gong Sun-Yaoyi added an explanation.

"Ah. When I first came in here, I saw a beggar lying crouched beside the entrance to the inn. They must have been trained in martial arts, but so the servers didn't dare to touch them. They just begged to be left alone. I guess they're still like that."

"Ah. Sister. That's a tactic often used by beggars who have mastered martial arts. They lie down at the entrance of a store and disrupt business. It's also a form of intimidation, demanding food or money."

"Oh. I know. I’ve had that happen a few times, um. No."

It's a technique that Qing also used several times.

Of course, it's not to the extent of interfering with business, but just to the extent of timidly loitering around when a party was held.

They say that if a plague ghost (plague ghost) comes, good fortune will run away or something?

If she was unlucky, she would get beaten up badly, but if she was lucky, she would get a bowlful of leftover food and pour it on top.

Since the bowl was probably family property, it would not have been possible to hand it over to the servants at will, and it was understandable that they only scattered food.

But isn't that much more humane than beating someone with a stick?

\textit{Well. Now that I think about it, they were really fucking bastards.}

\textit{Since it's Liaoning Province, if I ask Lady Murong to help me out a little, she'll probably help me out.}

\textit{No, not by any extreme means such as killing or crippling someone, but just taking their bowls.}

\textit{Revenge was mine, I must do it.}

\textit{On the day the Divine Thief appears, know that there will be no difference between rich and poor in the land of Jianping.}

\textit{We must achieve true redistribution of wealth.}

Seeing her not forgetting his grudge and swearing revenge anew, it was clear that she'd do it on her own without asking for help from others!

Now, Qing can be said to be a proper person from Zhongyuan.

"Well. But still, the inn was doing business normally, so you shouldn't be acting up. What kind of person were you?"

Qing's voice was sharp.

Beggars have been the long-time enemies of the Qing, so even if they were from Beggars Gang, they were not viewed favorably.

"Mada-, no, Heavenly Blossom Sword. Don't do that. My subordinates will handle it. Just wait a moment."

"Hey. It's okay. It's just that the thing I hate the most was being a beggar who's learned martial arts. Why would you go around begging after learning martial arts?"

Peng Daesan shoots her a look of disbelief, but since the flower beggar was already a strange person who disappeared into history, Qing remained confident.

So Qing rolled up her sleeves and chuckled.

As soon as you open the door to the guest house, a small front yard and a small inn in front of the gate come into view.

"Hey, I’ve set the table here, so go eat in a corner over there. There’s a noble person inside, so if you keep doing this, you’ll end up disturbing her!"

Still, seeing him prepared a table and then offered food, she thought the kindness of the server was truly generous.

If someone was kind, you should be grateful. Why were you insisting on asking for more?

Qing approached with quick steps.

\textit{Let me see what kind of beggar you are.}

\textit{Hmm. Why are their face looked familiar?}

"Ah. Young Lady Ximen."

"Uh. Hello?"

"No."

A subtle shadow fell between Xue-i-ri's eyebrows.

Murong Zhuji, who followed behind, tried to stop Qing, but immediately recognized her by her rare silver hair color.

"Young Lady? Do you know her? Isn't that Snow Flower? What? You suddenly became a beggar. Did the Ice Palace collapse in the meantime?"

"Yes. No. No."

"I know her, she's not a beggar, and the Ice Palace didn't collapse. Hmm. Was that it? But why are you acting like a beggar? No, well, being a beggar was convenient…"

"Wait? Here? Here? What's the relationship between you two? You, Qing'er, come to think of it, you were always asking what was going on with the Snow Flower."

The child who entered the Arur position immediately growled.

But Xue-i-ri, in her own way, subtly deepens the cracks on both sides of her lips.

It was Xue-i-ri's awkward smile, the first she'd seen in a long time.