\chapter{A Loner's Journey To Solitary Sword (1)}

The Sapa people, also known as the Apostles, cannot understand the young men from prestigious families who have come forward to help Qing.

What the hell? What do you think these guys were missing that they're just being friendly with a disciple of the Divine Maiden Sect?

If we look at it from the perspective of the Sapa, the rank of the Divine Maiden Sect was ridiculously low, and even if we double the number of the Sado Twenty, it wasn't comaparable.

Of course, there were 10 generations of the old generation in the political world, so the 20 seats were full.

The Divine Maiden Sect was famous simply as a sect of women, but if you looked at it by rank, it has major flaws in terms of scale and power.

If a divine dragon came from such a place, wouldn't it be right for the existing Ten Noble Families to treat her like a stranger, secretly despisde her, and restrained and sabotaged her, and at best, eliminated her?

In the end, when they grow up, they will be the masters who will challenge them, and also the new powers.

If Qing heard this, she would clicked her tongue.

Ha. Sapa level. Well, that's what you guys were like. Well.

Of course, Sapa can also feel wronged.

How proud was it that the political factions have gathered together and established their own territory, saying, "We were the others."

It's not a question of good and evil, it's just a question of where our goodness lies.

In a world where sects were growing in chaos, eating each other, there was no one else they can trust except me.

So I do my work without worrying about what others think.

But what about the political parties already?

Due to our nature, where other factions cannot covet the benefits already held by one faction, there can be no movement up or down the hierarchy.

If it hadn't been completely ruined, the Yun Family of Jin Province would still have a place in the Ten Noble Families.

A hundred years ago, the Five Great Families were the Five Great Families, and even before that, the Gupaeilbang existed as the Gupaeilbang.

And the leader of Wulin was Shaolin Temple, so much so that it was even called the Thousand-Year Shaolin.

Isn't it the perfect completion of a class system with no change in rank for a long period of time?

So, when a powerful, peerless swordsman like Heavenly Blossom Sword appears, shouldn't she be kept in check?

Instead the Five Noble Family heirs jumped into a life-or-death situation without even revealing their name or affiliation, so it seems they really risked their life.

Why on earth? What's so pretty about it?

"Hmm. She’s pretty, but she’s so beautiful that even Xishi couldn't compare."

"Ah. Was that why? If he's a man, then yes. But there were also that woman from Tang family. A woman who's captivated by another woman's beauty?"

"Don’t you know Jade Kilin? She must have followed Jade KIlin."

"If she came because she's in love with Jade Kirin, shouldn't she sabotage her instead? You should eliminate your rival immediately. If I were her, I'd take advantage of any opening without hesitation and launch a venomous attack."

"……? By the way, didn’t you say your wife was a widow? That her husband died of a strange disease?"

"Haha. That guy. That’s what he says."

The Divine Maiden Sect was less scary.

They say there was a Female Mad Dog who was the best female martial artist, but it was only one person, and those who remembered that notoriety were only very old masters.

Even the average lifespan of the Sapha warriors was seriously lower than that of the Jeongpa.

The story of the number one female martial artist was already a story from a long, long time ago.

But the Five Noble Families were scary.

Tang Clan and Peng Family? Although the Zhuge Clan was a bit easy.

The fact that the Zhuge Clan did not become famous for their martial arts was also the reason why the Zhuge Clan have been angry for generations and shouted, 'We too have martial arts and were strong! The Five Great Clans didn't get their ancestors' blood money!'

So the avengers wait for tomorrow.

How can anyone say they want revenge after seeing that list of names?

In Zhongyuan, resentment was ultimately an act of applause for those who resolve it, so even if the current situation was long, the time will come someday.

And, the non-avengers were raising expectations.

In fact, the density of avengers among the gathered martial artist was not that high.

The rest were explorers of the new art who still can't give up their obsession with the Essence Absorption.

Most of the people who followed Qing around don't even know that they have a grudge against her.

Because they believed that the raid on the hidden tomb was a conspiracy of the Blood Cult.

The control room was discovered by those who were searching through the empty shrine of the Blood Cult, and the writing of the Blood Cult's Heavenly King, and the true form of the Blood Cult witch was revealed there. By now, everyone was aware of it and thinks, 'Oh, it really was the Blood Cult. What a pity.'

But?

Isn't the Divine Art a separate issue?

After all, the truth about the Essence Absorption has not yet been revealed.

If there really was an Essence Absorption, then the Cheonhwa Sword at the center of it would have taken it.

She said she tried to get rid of it, but if the original divine art of Da Da Ikseon and the magic of absorption existed, how could a person without power be able to erase such a powerful martial art?

Or, you can take it to that well-known political party and have them re interpret and correct it, or even if it was not a political party, you can try to solve it with the power of a monk.

If you hear the sound of your chest pounding, you will feel suffocated, no, it will make your chest thump, thump, thump.

But humans were always like this.

Even in Qing's hometown, stocks and coins were creatures that, once they got addicted, considered it a realm of faith rather than analysis, and even though they knew it was a scam, they said that they could eat it and get addicted.

But was the Essence Absorption an ordinary martial art?

The best in Wulin!

The best master in the world at the time!

This was the strongest magic ever to guarantee this.

Turn your life around in one go!

Even well-educated people would be shocked by a single shot, and even the uncivilized people of this uncivilized era, who had no formal education, would naturally turned a blind eye.

The existence of the Essence Absorption has not been confirmed.

Since its absence could not be proven, its existence could not be confirmed.

However, the Essence Absorption did existed.

The Essence Absorption Art had to exist because it had to exist at the time and because the person who had to exist wanted it to exist.

It was a very clear truth to them.

For some people, the Earth was flat.

Some seriously retarded people believe that all of humanity was a single race, all descendants of Hwan-guk and Danguk, and claim that this was proven by an alternative history novel published in 1979.

A much older watermelon would be better.

Or maybe snake monsters ruled the world.

Is there another human race living beneath the earth?

It's as if they believe that if you draw blood on the floor and decorate it with special parts of all kinds of creatures, the Demon King will somehow grant you strength.

But, having been deceived by the Heavenly Blossom Sword's strange tongue, they ended up not being able to even challenge anyone who wasn't their enemy.

In the first place, in a life-or-death fight where if you win, your opponent dies, and if you lose, you die, do you have time to ask, 'I demand the truth from Heavenly Blossom Sword'?

But, as the foolishness continued to chase after it, didn't a major variable occur?

Maybe those guys will fight over the new skill, and if it's a magic absorption skill, wouldn't even the Jeongpa guys be drooling over it?

Now that the fate of life and death has been sealed, Heavenly Blossom Sword will never be able to keep his mouth shut even after death.

Since the Heavenly Blossom Sword won't be able to maintain her strength for a thousand years, there's still a chance.

For this reason, Qing's group felt comfortable.

Qing had a great time and ate well.

Well, there was someone who treated me well.

"Haha, looking at the friends of the Cheonhwa Sword, they were so handsome and beautiful. The future of Wulin was here, and the road to Jeongdo was as bright as the sun, without a shadow! Although the military and martial arts world were different, they were righteous heroess who wishes for the peace of the country and protect it. How could this general not offer this to his comrades who share the same purpose? Come, take a drink!"

"Your logic was quite extraordinary. You were truly a remarkable orator. Ah, of course, you were no match for Sister."

Qing chuckled at the commentary coming from beside her.

It was a drink that the general himself personally went around and poured.

What martial artist in the world would ever receive alcohol from a general?

However, Tang Lan-Ah was the unofficial princess of Sichuan who was basically worshipped.

She quickly noticed the subtle difference in politeness between how the general treated Qing and how he treated herself.

So after the general passed, they whispered.

"Qing'er, how do you know that man? Why does he acted like a servant?"

"Uh, um. My mother was an acquaintance of him."

"Huh? You said you don’t have a mom?"

If other people heard it, they would think it was too harsh.

But Qing hadn't seen Tang Lan-ah just once or twice.

This was not intended to be insulting, but rather a confirmation of the facts.

This was probably because, as a child whose actions were originally connected to the spine, the brain has no influence whatsoever on her words and actions.

In fact, if Qing's judgment was correct, how was it that Tang Lan-ah, who lives by spinal reflexes, was still alive?

That's because she believes in the ultimate finishing move of Mancheonhwaru, and once she commits it, she would be unconditionally forgiven.

"No, who in the world doesn't have a mother? Suddenly appearing in the world, um…"

\textit{Hmm. There's someone here who just popped out of nowhere.}

Qing, who was confused by her own words, gulped down her alcohol.

Due to the limitations of the still primitive method of making alcohol, all strong alcohol was expensive and good.

It's so frustrating to have a hot cycle with no real impact.

"I don’t know for sure. She claims to be my mother, so I’m sure it’s not a lie."

"Then why does he calls you Madam? Judging by the way that general acts, I guess she must be a very high-ranking person."

"Hmm. It’s a bit complicated."

"Why? Was she trying to manipulate you, or was she just asking for gold? Or was she trying to send her daughter away to a marriage now that she've found you?"

"No, that’s not it. She’s a nice person."

"Then what’s so complicated? Isn’t something good just good?"

\textit{Come to think of it, I will be seeing Her Majesty the Empress soon.}

\textit{Of course, they would know since I used the Empress's Seal to mobilized the military.}

If Princess Yeonsul dies and the body she left behind was hers, Qing was willing to be her replacement.

She might be nothing more than a substitute for a mother who has lost her child, but she was not going to enter the palace, so she'll just meet the Empress once in a while and shows her some jokes.

But what if that's not the case?

What if Yeonsul was alive?

The Empress's daughter was barely alive, breathing, and what if she took possession of her body?

Then that won't work.

\textit{Hmm. I don't know.}

\textit{Think about what happens then.}

\textit{There were things that need to be resolved sooner than that.}

\textit{No, how do I get them off?}

This was the priority that Qing must considered now.

\textit{It's obvious that these guys will just stick to me like leeches.}

\textit{It doesn't seem like they'll go just because I tell them to.}

\textit{If that were the case, they wouldn't have interfered in the life-or-death decision, and at the very least, they would have told me to step down and reveal their Five Great Families  background before the battle.}

\textit{I am so grateful for your willingness to fight together.}

\textit{Wouldn't that be an excessive favor?}

\textit{But, you guys were really weak…}

There were more than a few people who secretly used poison in life and death situations, but Qing was already immune to the poison due to the blood poison, so she's not worried about that.

\textit{If I think about it, thanks to that, no one ran away during the life-or-death struggle, so I think it was probably because they thought I wouldn't last long after being stung by the poison.}

\textit{Is it only poison?}

\textit{If you work as a doctor, isn't it like an uncivilized, primitive era where you could die from infection if you were unlucky even if you were pricked by a thorn?}

\textit{Does that mean he's strong?}

\textit{Is the realm high?}

\textit{I'm so anxious, what can I do?}

\textit{In the first place, if you're friends, you're friends. There's no need to follow each other around and go through all the important things together.}

\textit{It's not like people would flock to a wedding or a funeral just because something happened.}

\textit{It's nice and happy to see my friends since my accident was like this, but, um, uhm.}

\textit{So how on earth can we break up without hurting each other's feelings?}

Qing thinked so fiercely.

But since Qing was strong when it comes to malice but weak when it comes to kindness, she didn't know what to do about this.

It was during that time.

The orderly who was supposed to be in charge of all the practical work under the general, Yang Sa-mok, came up to her and gave a report.

"Excuse me, there were people who claim to be Madam's friends waiting in front of the restaurant."