\chapter{Drifting Off Course (8)}

Choi Yangsu, the branch manager of the Jangheung Trading Company's Naknyeong branch, was extremely ill at ease, sitting on pins and needles, or as they say in Zhongyuan, lying on a bed of logs.

Even if news traveled slowly in Zhongyuan, how could it be slow even in a neighborhood where trading companies and manors were concentrated?

Moreover, merchants were a breed that basically kept their ears wide open, always on the lookout for opportunities to make money.

Even so, this was a chance that came perhaps once every ten years.

Wasn't this the time when grain turned directly into gold?

At such an opportune moment, he heard the news that a chain-relief horse1 was sweeping through the trading companies one by one, so of course, he couldn't sit still. Naturally, he was anxious and uneasy.

Still, he had made a lot of preparations.

Unlike the small-time trading companies in the Naknyeong area, the Great Jangheung Trading Company was the number one trading company in Shaanxi Province, a merchant renowned throughout the world.

Therefore, unlike other hole-in-the-wall businesses, their relationship with the government was incredibly close, so much so that the magistrate of Naknyeong had personally agreed to block the main gate with his constables.

"Branch Manager!"

"Yes, did she leave? Did that bitch leave?!"

"Well, she has entered the manor grounds-"

"What?! How?! The magistrate promised to guard the entrance!"

"The Magistrate is still guarding the entrance as we speak, but that bitch tore down the wall and entered……"

The Branch Manager's chest felt like it was about to burst.

To think she would tear down the wall and enter, wasn't that something only a band of bandits would do?

No, even bandits wouldn't tear down the wall; they would either go through the entrance or climb over the wall, not outright destroy it and invade.

"That doesn't make, wait, you said the magistrate is guarding the entrance? Still?"

"Yes. He said he would continue to guard the entrance as promised……"

The Branch Manager's chest felt like it was about to burst for an entirely different reason.

He had asked the magistrate to guard the entrance, but even now, when the bandits had already invaded, he was still guarding just the entrance.

It was an unspoken pressure, implying that since he had fulfilled the request, he expected a strict payment in return.

When the very bandits they asked to be guarded were just watching, the long-standing adage of merchants to not associate with government officials had a reason it had been passed down for so long.

As the Branch Manager pounded his chest, his subordinate tried to comfort him.

"Still, didn't you call all the first-rate disciples of the Naknyeong Martial Hall? No one in Naknyeong will dare to defy the Naknyeong Martial Hall."

"Branch Manager!"

No sooner had he finished speaking than another employee rushed in.

As soon as the Branch Manager saw the employee's expression, he felt as if he had already heard the report.

"Haa. Why? Did the bandits just walk right past them?"

"Th-That's. It seems they were already acquainted."

"What? These small-town martial halls. I didn't expect much from them to begin with. They're just good at wagging their tails whenever a somewhat renowned figure comes around."

Still, since it was best to give gold and silver to the Naknyeong Martial Hall if he wanted to do business in Naknyeong, he had merely borrowed the prestige of the best martial hall in the area.

Rather, what he was counting on was something else.

"What about the Elder?"

"He should be facing that bitch right about now."

"Right. If it's the Elder, then."

The Elder was an Unrestrained Realm Master, a peerless expert formerly renowned throughout Zhongyuan.

There was no way that such a brazen, wicked, outrageous, and ignorant young girl could stand a chance.

The Branch Manager's expression relaxed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In Zhongyuan, there was a saying, 'One man can face ten thousand'.

It meant that one person could face ten thousand, and it originally referred to the famous Xiang Yu, the greatest and most unprecedented war machine in Zhongyuan.

Xiang Yu was not only outstanding in his individual martial prowess but also a true god of war who had reached the pinnacle of strategy and tactics.

It was just that he was a bit too oblivious, wanting to solve everything through war, which ultimately led to his downfall.

Anyway, this was exactly the kind of situation that brought to mind the saying 'One man can face ten thousand'.

The aura exuded by a single Supreme Master was enough to extinguish the fervor of a crowd that had been greatly agitated, like a candle before a gust of wind.

Qing carefully examined the old Master's face, trying to discern the number that would appear. He was neither particularly good nor evil.

Qing was originally kind to people.

Since those with high Evil Karma were not considered human to begin with, Qing was always kind to people.

Unless their first impression was extremely bitchy, she knew how to be polite, a rare cultured individual in the Middle Ages.

Qing clasped her hands together and bowed.

"Greetings. This girl is called Ximen Qing. May I ask for the Elder's name?"

Her polite attitude softened the old man's aura a bit.

"This old man is called Yuradal."

At that, a gasp was heard.

A famous person? I don't know who that is……

However, there was a way to deal with such situations.

Qing inhaled, then exhaled in time with the others.

"Yuradal!" "The Heavenly Wanderer!" "The Nine-Sectioned Wanderer!"

It was a simple trick; if you didn't know, just shout their name and you would seem like you knew.

It was impolite not to acknowledge a famous person, so even though Qing had no idea who he was, she pretended to know him.

She was a bit unsure whether he was at the end of the Transcendent Realm or beyond the Unrestrained Realm, but judging from the reaction, it seemed he was an Unrestrained Realm Master.

Although Qing was not aware, Yuradal was originally an incredibly renowned figure.

This was more due to his background than his skill, and as his moniker suggested, he was a wanderer.

The Heavenly Wanderer referred to the five strongest wanderers known, and even being the last among them meant he was considered the fifth best among all wanderers in Zhongyuan.

However, Qing did not know.

All she knew was that the old man was a famous Master that everyone seemed to know.

And that was a fact she had just learned.

And his Evil Karma was thirty-six.

For a swordsman, thirty-six was considerably virtuous, so he wasn't a bad old man.

That was why Qing tried to initiate a conversation, or rather, start talking some shit.

"Elder, there is a great disaster in the city right now-"

"Stop. This old man does not know of such things."

Yuradal, who had inadvertently blocked Qing's hellish mouth beforehand, continued.

"As you know, this old man is a wanderer. A wanderer is but a sword hired for a price. Does a sword discriminate between people? I have already been amply paid, so I am merely a sword to be wielded in their hand."

It was exactly what an old wanderer would say.

It was a statement full of pride that could only be made after having lived as a wanderer for a long time.

"I have been asked to let no one pass, so I shall do so. If you wish to pass, must you not resolve this as a martial artist?"

As he spoke, he grasped the sword handle at his waist and drew it. But the blade kept coming out, continuously being pulled out with a clatter.

Thus, what fell to the ground were nine iron segments connected together, a unique weapon known as a nine-section whip.

It was also the unique weapon that earned Yuradal the title of Nine-Sectioned Wanderer.

A martial artist should resolve things as a martial artist.

Of course, he was right, but…

Qing asked in bewilderment.

"Elder? Have you not already surpassed the Unrestrained Realm? I thought you would normally yield ten moves or so."

"Keke. Was this old man an Unrestrained Realm Master since birth? What reason is there to impose hardships on myself just because I have lived long and grown old?"

"Yes……."

He's a wanderer, huh?

That's true, but it also feels incredibly petty.

Honestly, if you asked whether she was confident or not, of course, she was.

She had taken down a Transcendent Realm Master before, so there was no reason she couldn't do it again, now that she was also in the Transcendent Realm.

Of course, she remembered that the Unrestrained Realm Master back then was as solid as a rock but also slow or something like that.

But now I can also use Sword Force, you know.

Qing clasped her hands and spoke.

"This one is a latecomer to the martial world, an external disciple of the Divine Maiden Sect, Ximen Qing. I seek the Elder's teachings."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"By the way, how much does it cost to hire an expert of the Nine-Sectioned Wanderer's caliber as a guest retainer?"

The subordinate, who had suddenly become curious, asked the much more relaxed Branch Manager.

Originally, merchants were those who desired to be the head of a snake rather than the tail of a dragon.

Instead of working under someone, they preferred to one day become independent and start their own small trading company.

Of course, the best-case scenario was to work under someone and then take over, but that was practically impossible for a huge trading company like the Jangheung Trading Company.

So, while working under someone, one had to learn as much about business as possible. As such, his question was about how much money it took to employ an Unrestrained Realm Master.

"To hire a known expert, gold and silver are not enough. No matter where they go, an expert who can make gold and silver flow in will not be swayed by mere money."

"Then how did the Elder……?"

"Ahem. It was about trust. A woman once came to the trading company carrying a sick child and boldly claimed that this child was of the Nine-Sectioned Wanderer's bloodline, and that curing the child would erase a great debt."

"No way, did such fortune just roll in by itself?"

"But catching the fortune that rolls in is the true skill. Ahem."

The Branch Manager cleared his throat and lowered his voice.

"If a beggar in rags came to you and claimed that her child was the offspring of a peerless expert, would you have believed her and treated the child? Moreover, she was a cheap prostitute that even the gatekeepers knew. It wasn't even someone he didn't know."

"Hmm. Still, what does the treatment cost? If you can employ a peerless expert with that little money, it's quite a bargain, isn't it?"

"Tsk tsk. You say that because you already heard the story. If a prostitute you know well comes to you and claims that her daughter is actually the offspring of a peerless expert, would you believe her? How many swindlers come to a trading company? They range from medicine peddlers claiming to have concocted great elixirs, to those selling family heirlooms, or those with good business opportunities.

What about those who claim to have found a gold mine and demand investment?

Scammers claiming to have obtained a treasure map are a dime a dozen, with at least one visiting every month.

"So the insight of the owner, who was able to distinguish between lies and truth, was what truly shined. If not…"

If not, even if it was a lie, since the sick one was a girl, he might have thought that he could recoup the investment later.

The Branch Manager swallowed the latter part of his words.

In any case, after that, when the Nine-Sectioned Wanderer appeared in Chang'an, he met with the alleged daughter…

Whether it was the instinct of a father, or if he had some other way of knowing, or if he was just lonely in his later years and decided to treat her as his daughter, she shed the label of an alleged daughter and truly became his daughter.

And then Yuradal spoke.

'This old man was foolish and did not know he had his own flesh and blood, and even worse, I almost did not know that I nearly lost her to a mere trivial fever. I have received the price of my daughter's life in advance, so as a wanderer, I will continue to repay it.'

-He said something like that.

"Ooh. What a great story."

"Right? Moreover, he has been staying at the trading company as a guest retainer for over five years already. Yet he still says that the debt for his daughter's life remains, so I can't help but admire the owner's virtue."

So the Branch Manager had also relaxed.

After all, who could possibly abandon the grace of saving one's child?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Yuradal hesitated.

"Wait. The Divine Maiden Sect? How can a disciple of the Divine Maiden Sect wander around alone? Isn't it a mysterious sect that severs ties with the secular world once one enters?"

"This girl is merely a disciple with the surname Ximen, taught by Daoist Ximen Surin. I have not entered the Divine Maiden Sect, so I can do as such. Moreover, if a disciple who can protect herself wishes, she can receive permission to descend the mountain."

The Divine Maiden Sect was not a completely closed-off sect.

Once one reached the level of a first-rate disciple, they could go out when they wanted with permission.

After all, how could incidents where Divine Maiden Sect disciples fell in love with men and gave up their names happen?

Since it was impossible to meet men in the Divine Maiden Peak, a sacred ground where men were forbidden, they obviously met them while going out to play.

Yuradal's expression hardened even more.

"Wait. Did you just say… You are Senior Ximen's direct disciple?"

A direct disciple referred to a form of apprenticeship where the master accepted a disciple but maintained a distance from the sect.

Naturally, one must not teach the secret techniques of the sect.

Since it meant that they had accepted the disciple despite not being able to bring them into the sect for some reason, direct disciples were usually particularly close with their masters.

Other peculiar types of disciples included Lineal Disciples and Named Disciples.

A Lineal Disciple was a successor who would inherit everything from the master.

In contrast, a Named Disciple was a sham.

They only borrowed the master's name.

What was the point of that, one might ask? In Buddhist or Daoist sects, it was common for people to enter to learn the basics for half a year or a year and then receive a Daoist or Buddhist name before leaving.

If Qing had heard this, she would have exclaimed, 'Wow, a temple stay!' Indeed, the concept was roughly similar.

At any rate, at the mention of Senior Ximen, Qing's eyes widened.

Wait, are they acquaintances?

"Ah. Do you know my master?"

"Ahem. No. You should have said that earlier."

Yuradal struck a pose and swung his nine-section whip, the long weapon coiling around his waist with a clatter, leaving only the handle visible. 