\chapter{Drifting Off Course (6)}

When people saw Qing, they would often cough and clear their throats before speaking.

The reason was simple.

They would be entranced by her face at first, but then they would realize it was a great discourtesy or an absentminded act, so they coughed once out of embarrassment.

The head of the Great Completion Commerce was no exception, so even though she was an unwelcome guest, when he saw her gracious beauty, he momentarily forgot what to say, so he had to cough to cover the silence.

"Ahem. I am Joso, the head of the Great Completion Commerce."

"I'm Ximen Qing. Sir, right now in the city-"

Qing was about to cut to the chase and get straight to the point.

However, a head of a commerce was not someone to be taken lightly, so he cut off Qing's words and spoke.

"Listen, according to the law, gatherings of more than 50 men without prior notice, except for weddings, funerals, ancestral rites, and mutual aid, are considered rebellion. It seems you are unaware of this law, Young Lady, but this is a grave offense."

Do you know you're not supposed to gather people like this?

It meant that if they dispersed now, he would pretend not to have seen anything, so they should scram.

Qing replied.

"Sir. We have come to purchase grain for relief efforts."

The head's face contorted.

Qing's response was to pretend she hadn't heard.

One might seriously wonder if she had thought about it and then decided not to speak up, such was the perfection of her act of ignoring him.

"Is there a disaster in the city right now-"

"No, wait, did you not hear me? It's a big deal to gather people like this, I'm telling you."

"We're trying to provide relief grain, but the quantity from the Clear Stream Group is not enough to last even a few days. I will generously offer double the market price. Will you sell all the grain you have?"

In the end, Qing finished what she had to say.

"Listen, the law is strict-"

"Sir? Will you sell your grain? I'll add nine more tenths to the market price."

"I said, it's going to be a big deal if you gather like this!"

"Sir? I'll add eight more tenths to the market price. Sir? Are you not understanding me right now? How gracious of you to offer to do it for even cheaper."

With each sentence, the price dropped by one-tenth.

At this, the head jumped.

"What are you saying! Right now, we're trading at a gold piece per seom, how can I possibly at that price-"

"Six-tenths. Ah! That's right."

Qing suddenly raised her sword.

"I don't think I showed you this properly since you seemed to have trouble calculating. Here. Look. Sword Force. Sparkle, sparkle."

Qing lifted her Moonlight Sword (No. 8) and showed off the sunset-colored Sword Force.

The head's heart sank.

This bitch has come here fully intending to threaten us.

"Sir? Since you are here, does that mean that this, what was it called again, Taran?"

"It's the Great Completion Commerce."

"Yes. Since the Great Completion Commerce is here in Luoning, does it mean that it arose and settled in Luoning? Are you from Luoning?"

"……That is so."

"Then we are all neighbors and the current success of the commerce has come from Luoning, but when the city is in great distress, are you saying you will take advantage by raising the price of your precious grain?"

"Listen, it's not that, it's just that the price of a commodity rises the rarer it gets. Right now-"

"Sir? There are many ears listening, you know? You should be careful what you say?"

At that, the head swallowed his words and looked behind Qing at the crowd that had gathered like a cloud.

With a subtle rage in their eyes, if he said he wouldn't sell, they might go back for now, but he wouldn't be able to move comfortably in Luoning in the future.

"Now. This is my final request. I will offer you double the market price. As far as I know, the market price already includes a profit, so if I offer double, won't that be a great profit for you, Sir?"

The head had never heard of a final request before in his life.

Before this, he had never even imagined such a terrible phrase could exist.

"That. I am."

The calculations of a merchant and a non-merchant were different.

If an item bought for one tael was sold for two taels, it was a profit of one tael.

But if that item could have been sold for ten taels, it was not a profit of one tael, but a loss of eight taels.

However, forget losses; if he refused, the aftermath would be, based on her momentum, not an aftermath but an immediate siege, so it should be called a present haphazards rather than future troubles.

"Alright. I will offer double the market price."

At that, Qing smiled brightly and politely clasped her hands.

"Thank you for your decision for the city. Now, everyone, here is the head who willingly gave up great profits for the city. Shall we all give our thanks together?"

"Thank you!"

"Thanks to you, we will live!"

At this, the people raised their voices in response.

"Ahem. No, well, it's nothing."

Although it was close to extortion, no, it was extortion, since she had acknowledged his merit and raised his honor, his reputation had actually risen.

Amidst the rising sounds of gratitude, the head's mind was filled with worries.

Perhaps I should just join the relief effort at this point. If I'm going to suffer losses anyway, wouldn't it be better to gain some goodwill……

However, even selling at double the price was still a good deal.

As Qing said, the market price already included a hefty profit, so double the market price meant a huge sum where the difference was entirely profit.

The head, torn between preserving profits or gaining goodwill, eventually decided to preserve profits.

Of course, not all merchant leaders were like that.

"You are doing a good deed! Our Willow Commerce will follow Young Lady Ximen's will and lend a hand to the relief effort!"

As Qing toured the merchant's street and bought grain, some merchants with smaller stocks offered to give it away for free, saying to use it for the cause.

Even on the merchant's street, everyone had eyes and ears, and as she took her time visiting each one, they heard the news from those she had already visited. As such, everyone was already waiting with a decision made, wondering when their turn would come.

So, after finishing the tour to the left of the Clear Stream Group and heading to the right, she stopped at the next manor.

But for some reason, the next gate was quite far.

It meant that the manor was that much larger.

And from behind came whispers.

"Isn't the next one the Jangheung Group?"

"Hmm. Is it okay?"

"What's the big deal about Jangheung Group when a Fairy is visiting?"

"Still……"

At this, Qing asked Geol Taran.

"When the talk of Jangheung Group comes up, everyone seems a bit, well, hesitant? Is it that big of a group?"

"The Jangheung Group is also famous for being the greatest merchant group in Shaanxi."

She didn't know, but a huge merchant group that had a firm grip on an entire province.

After all, a merchant group capable of undertaking a river improvement project could not possibly be a small, insignificant hole-in-the-wall operation that just connected a few cities.

"That's just saying they're loaded with money, isn't it?"

"Miss, if you have a lot of money, your backing is also bound to be great. They say they've poured so much money into the government that the leader of the group is rumored to be sworn brothers with the Provincial Governor of Shaanxi."

"Ah. They're in bed with the government? They must have taken on the river improvement project through connections, huh? Ah. Indeed."

Qing understood at once.

Tap tap tap Qing reached the top of the hill and a wide view opened up, with soldiers in formation, holding spears, blocking the road.

And in the lead, a middle-aged man wearing a hero's headband saw Qing and, after momentarily losing his mind at her beauty, cleared his throat as usual and spoke.

"Ahem, halt!"

At that, Qing obediently stopped walking.

Since she had stopped, she kept her mouth moving.

"This young lady is called Ximen Qing. May I ask who you are, Sir?"

"Insolence! How dare you not show respect to the Magistrate!"

Unexpectedly, the answer came from the man standing to his right.

A magistrate was roughly the equivalent of a deputy mayor of a city.

And the guy who just shouted was probably someone who assists with miscellaneous tasks and flatters his superior.

"You are a Magistrate, I see."

Qing made a fist-palm salute.

At this, the man on the right flared up again-

"Insolence! How dare you not kneel before the authority bestowed by His Imperial Majesty!"

Originally, the authorities' way of asserting dominance was to make people kneel under the solemn authority of the Emperor before starting the conversation.

But to be precise, there was no reason for ordinary people to kneel if they weren't carrying out an imperial order. Well, there was a reason, actually.

If you didn't kneel, you'd get arrested.

Honestly, Qing's knees were cheap.

To Qing, kneeling was merely a single step taken to gain momentum, a stance taken to fire off with her superhuman leg strength.

However, since the Magistrate and the lackey on his right were covered in Evil Karma, no different from bandits, there was no reason to kneel and rely on such momentum for these insignificant villains.

"No, thank you?"

"What, what!? How dare you violate the authority of His Imperial Majesty with such a lowly status! This is treason, treason! Ever since you gathered the commoners and dragged them around, I knew it!"

"That's strange. So, are you saying that I should show respect to the Magistrate, who is here, as if to His Imperial Majesty? So, the Magistrate and His Imperial Majesty! are at the same level, is that what you're saying? Wow, isn't this treason?"

"Wh-Who said such a thing!?"

"Everyone! Here, the Magistrate is demanding the same respect as one would give to the imperial family! My goodness, in my life, I've never heard of a mere city Magistrate demanding the authority of the Son of Heaven and to prostrate before him! I wonder who would dare harbor such treasonous intent!?"

While leisurely smiling and observing, the Magistrate's face instantly drained of color.

"Wait! I never, I never had such thoughts, not even for a moment!"

"Then why do you demand such prostration! This is the utmost respect shown only to the Son of Heaven, the owner of all under heaven! Now, are you saying that you are in the same position as the august Emperor, that you are the Emperor in this Luoning land! Is that what you're saying?!"

A tongue could be a deadly weapon, too.

It wasn't about stabbing with Sword Qi imbued in the tongue, but rather that the words coming out in front of so many onlookers would soon become rumors that spread far and wide.

To stop such rumors, someone as powerful as the Emperor himself would have to completely annihilate everyone who heard them with a rain of cannon fire.

"No, slander, it's slander!"

"Slander, you say. Then, the person on your right is now framing the Magistrate for treason by fabricating words! That guy was the traitor!"

At that, the man on the right leaped up.

"No, you're making strange-"

"Magistrate? What are you doing? With a treasonous criminal by your side, no less. Could it be that you are harboring such a wicked traitor for a different reason? Could it be, you too harbor treasonous intent?"

"S-Such dreadful words should not be spoken so carelessly! No matter what anyone says, my utmost loyalty is already like a great mountain!"

"Then why do you keep that insidious traitor by your side? Don't you have soldiers behind you? Why don't you imprison him right now? The only reason I can think of is that you, too, harbor treasonous intent."

"Y-You there! Seize this man at once!"

"Oh my, Sir! I am wronged! Don't you know! I only-"

"Hey, shut up! Whether you are guilty or not will be revealed later! For now, quietly accept your arrest!"

Qing watched the spectacle with a crooked gaze.

From the start, blocking the road like this was extremely suspicious.

While she was trying to buy grain for relief efforts, these government officials, instead of helping, were standing guard to protect the Jangheung Group or whatever, so naturally, she was incensed.

"I am wronged! Sir, siiiir!"

As the lackey was dragged away, Qing finally smiled and spoke.

"Well then, Magistrate. This young lady only has business with the Jangheung Group, so would you please move aside?" 
