\chapter{Drifting Off Course (9)}

Yoo Radal was currently serving as a guest warrior for the Jangheung Trading Company, working off the debt he owed for his daughter's life.

Originally, Yoo Radal was a man who was meticulous about calculations.

But when it came to the price of his daughter's life, he couldn't determine how much it was worth.

However, he thought that since it was his daughter's life, the higher the price, the better.

It wasn't that the treatment from the Jangheung Trading Company was unsatisfactory.

But a master of the Unrestrained Realm was worth more than what the trading company was paying him.

So he was constantly working off the difference, paying off the debt.

And that was why Yoo Radal stayed.

He had already been there for over five years.

He thought that someday he might think that this was enough and that it was time to leave, having settled the accounts. He decided to stay until he had such thoughts.

And now was the time for such thoughts.

Hmm. Isn't this enough to pay for my daughter's life?

Yoo Radal was old, and an old man's Wulin was stuck in the memories of his prime, long past.

At that time, Ximen Surin hadn't entered seclusion yet and was still active, albeit past her peak.

Yoo Radal could summarize Ximen Surin in one line.

The most narrow-minded person with the longest-held grudges among all the masters under Heaven.

But in this situation, to incur the wrath of an absolute master with the worst personality in the world?

This didn't add up.

Come to think of it, although he was grateful that she saved his daughter, she hadn't really bestowed any great wealth or treasures.

It was just a fever that children often caught.

Of course, his daughter had survived because of that, so he considered the medical fees and the life debt separately.

Still, five years seemed like enough payment.

Moreover, staying as a guest warrior for so long meant that the world saw him as part of the trading company, and the benefits the Jangheung Trading Company gained from having an Unrestrained Realm Master as a backer were not small.

He must have established at least two pillars for the company, so this much should be more than enough to cover his daughter's life debt.

The reason he had stayed this long despite that was because the longer he stayed to pay off the debt, the more his daughter's value increased.

It was a fatherly love that made him stay put.

Even without that, the old wanderer was starting to feel restless, itching to travel.

Those who remained wanderers even in their old age were born with an insatiable wanderlust, unable to settle down in one place.

However, although the old man could wander with little time left to live, his daughter could not.

He had to find a good man and set her up with him.

He couldn't be a man like himself.

Not some ignorant fool who wielded a sword without knowing if his own flesh and blood were alive or dead, but a refined, capable man who would be devoted to his wife. A fine son-in-law, indeed.

So, the longer Yoo Radal stayed at the Jangheung Trading Company to pay off his daughter's life debt, the more his daughter's worth increased.

It was truly a wanderer's way of calculation.

But… This was enough.

And since it was the Divine Maiden Sect, he had something else to ask about as well.

"Child. Does the Divine Maiden Sect not accept named disciples? I was thinking of leaving my daughter there for about five years. And, um, then, wouldn't they teach her at least one martial art or something?"

At this, Qing thought to herself.

Oho. Is he suddenly asking about joining now?

"Elder. Of course, our Divine Maiden Sect does not turn away any woman who comes. However, we do not discriminate between the noble and the humble, and everyone must sweat, work, eat, and sleep together, so it might be quite arduous."

"I'm not asking you to treat her like some precious young lady. It's only natural for people to work as much as they receive. However, I heard that the martial arts of the Divine Maiden Sect are exceptionally beneficial for women."

He was referring to the Fairy Arts.

From the Inner Qi Cultivation Technique to swordsmanship and footwork, the martial arts of the Divine Maiden Sect all had the effect of Fairy Arts, which was why the basic appearance of the Divine Maiden Sect's disciples was so high.

"Ah. Yes. But isn't the Elder's martial prowess already renowned throughout the world for its excellence?"

"Don't even mention it. Each segment of the nine-section whip weighs over two geun, so the entire whip is almost twenty geun. What kind of weapon is this for a woman to handle? If I had known this would happen, I should have just learned the sword. It's a weapon that requires innate strength. Unless I meet someone who can inherit it later… Haa."

Yoo Radal let out a deep sigh.

"Even if I find a strong fellow, what's the use? No one even wants to learn such an unorthodox weapon. Well, isn't this why unorthodox weapons are gradually disappearing from Wulin? I never had any intention of forming a sect or anything, but it's a bit sad to see it disappear like this. Well, I can't say my feelings aren't complicated."

"Ah, yes……"

"My daughter is growing up, so now I'm thinking of finding a proper son-in-law somewhere. I can't keep taking my daughter everywhere with me. So I thought of asking the Divine Maiden Sect, but I don't know what else to do."

He wants to leave his daughter somewhere and go find a son-in-law.

Qing tilted her head.

Shouldn't the daughter choose her own husband? So she asked.

"Um. But if you're looking for a son-in-law, wouldn't it be better to find him together with your daughter?"

"……What blood ties mean is that my daughter is practically my spitting image. If I had long hair in my younger days, she would be me. When I saw my daughter, it was like, anyone can tell at a glance that she's my daughter."

Qing imagined a long-haired Yoo Radal.

Of course, since the person in front of her was an old man, the imagined long-haired Yoo Radal looked a bit horrifying.

"Um."

"So taking her with me to find a son-in-law would just be a hindrance. And if I don't want to hear her complain that her father passed on such an ugly appearance, I have to make sure she learns at least the Fairy Arts to a level of mastery."

What's this? Why is this suddenly a counseling session?

It seemed that concerns about a child's future were the same in Qing's homeland and in Zhongyuan, as Yoo Radal was full of worries about his daughter.

"Aigo. I don't know where to go to find a proper fellow. What was his name, that Wandering Saber Yeok Tae-gang? I heard he's a decent guy for a wanderer, but, um, still a wanderer, right? Wanderers are a breed that can't help but abandon their wives and children to roam outside."

"Oho."

Qing tilted her head.

Wandering Saber? I think I've heard that name somewhere?

Well, since it's a cool title like Wandering Saber, it's probably something I've heard in passing.

"Yes. So is there any decent young man you know? Someone moderately wealthy, moderately handsome. No, appearance doesn't matter that much. Someone diligent and loyal. Yes, loyalty. A loyal man is the real deal."

It was really turning into a counseling session.

"Well, Elder. I'm sorry to interrupt, but……"

"Ah. Right. Sigh. People will talk behind my back later. I'll have quite the damaged reputation in my old age. Well, I'm old, so what's the use of reputation… I'm a wanderer anyway, so what reputation do I have to even talk about……"

Thus, the Nine-Section Wanderer, Yoo Radal, kept muttering to himself as he turned and left.

What was that? Did I… defeat him?

He retreated on his own, so I guess I can pass, right?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Branch Manager! Trouble! Big trouble! Those bandits are now rushing towards the inner court!"

"What? How, wasn't the Elder blocking them?"

"Well, he said that since he had helped for over five years, he had paid his dues and was leaving…"

"No, why now of all times! Of all times!"

So those Wulin bastards are like this!

Especially those wanderer types!

The Branch Manager, still fuming, added another word.

"He should have finished what he started!"

It was a bit too much, no, extremely excessive to suddenly leave in the middle of something, saying he had done enough.

If he had paid off his debt, he should have asked for a wage afterward. How could he just leave when the fate of the trading company was hanging by a thread!

Of course, to be precise, only the fate of the Branch Manager was hanging by a thread.

Would a huge trading company representing a province really be affected by the ransacking of just one branch?

Moreover, Nakseong wasn't even the Jangheung Trading Company's home ground of Shaanxi.

But the Branch Manager who had his branch ransacked was screwed.

Did he need any other explanation?

Just like a carriage wheel that was replaced if it had a defect, a Branch Manager who couldn't protect his branch was defective, so he would just be replaced.

As the Branch Manager trembled, the sounds of people outside the main hall grew louder.

-Branch Manager? Hello? We know you're in there. Are you not coming out?

It was a voice as lovely as any in the world, but he never imagined that such a beautiful voice could be so terrifying.

-What's going on? Is there no one in charge here? Then, it wouldn't matter if we just ransacked the warehouse. Everyone, let's not take too much, just a little, only as much as each of us can carry, okay?

The words that didn't even wait for him to say he would hold out.

"Branch Manager?"

"Ugh. Since it has come to this… I've come this far from nothing, you know? If a merchant, then one must act like a merchant and negotiate."

Thus, the Branch Manager finally lifted his heavy behind.

He proudly opened the door of the main hall and strode out to face the crowd, shouting!

"Aigo, Sirs! This is not right. No matter who you are, whether your status is high or low, whether your house is large with many tiles or just a humble, tiny thatched hut, it is customary to send word in advance and receive permission before visiting, so how can you barge into a trading company leading so many people?"

Qing, who was watching the Branch Manager wailing as if he would prostrate himself on the floor, momentarily lost her words.

After a moment, she replied.

"Of course, I know it is not polite, but the city's floodgates have collapsed, and the city walls are crumbling. The damage is beyond words, and the grief is such that tears are flowing and pooling on the ground. At such a time, I am merely trying to offer a little comfort with good intentions."

"Aigo, Sir. Good intentions, of course, but why don't you make an appointment for later? After all, isn't a merchant's work all about resolving matters through conversation and negotiation?"

"Branch Manager? I hear that while the city is in disaster and people are starving without food, some beast-like sons of bitches are trying to take advantage by raising the price of grain thirty, forty, fifty times."

"Aigoooo, Sir, please listen to my plight. What power does a mere Branch Manager have to decide whether to release grain or not, to offer it cheaply or not? I'm just a servant who follows orders from the main company, so what can I do?"

It was a merchant's ultimate defense of claiming to have no authority.

I am merely a person who cannot decide anything.

So, go and make a decision with the higher-ups.

Of course, I do not know how to reach the higher-ups, so whether you can do so is up to you.

However, this method was only effective against a single, powerless customer.

Qing's tongue was a terrifying weapon that had even made the Tang Clan's Grand Elder open his pouch in admiration, and she had a crowd behind her, making her eloquence even more powerful.

Moreover, the Jangheung Trading Company had a black mark against them.

They tried to use the flood to raise the price of grain, hired Hyeonseung, mobilized the disciples of the top martial arts school in Nakseong, and even brought in an Unrestrained Realm Master.

Honestly, if they had used that much money for something else, wouldn't there have been more than enough to release all the grain?

Since merchants were stingy with their losses, they would obviously add the cost of defense to the price of grain, making it clear that they would act even more viciously. Thus, they already had a 100-fold black mark against them from the start.
