\chapter{Drifting Off Course (10)}

"Branch Manager? So, you are saying that the headquarters of the
Jangheung Trading Company directly ordered to exploit the cities
severely damaged by the flood by raising the price of grain by fifty
times. Are you saying that such instructions were clearly given?"

Some methods to win an argument.

Exaggerated interpretation. Using the opponent's argument.

Distort the opponent's argument, specify it, and nail it down.

And persuade the audience, not the opponent.

As Qing asked the question, the eyes of the crowd turned fierce.

"No, that's not it."

"Then what is it? Did the High Monk's visit have a customary display
of sincerity with a small amount of gold and silver? To make a profit
while spending so much gold and silver, wouldn't you have to engage
in such vicious business as collecting loan contracts, selling daughters
to brothels, selling sons as slaves, and ruining entire families?"

The Branch Manager was at a loss for words.

Because that was indeed their intention.

Qing's words were an exaggerated interpretation and a forced
argument, but in reality, this was precisely what merchants did when
disasters struck.

It was just that this time, the trading company had gotten ahead of
themselves, dreaming sweet dreams until Qing splashed cold water on
them, delivering a devastating slap.

It was said that a cow captures a mouse by walking backward, which
was exactly the case here.

Thus, the crowd's eyes became sharp like awls, as if they were on the
verge of piercing something.

"A misunderstanding, it's all a misunderstanding. The High Monk just
happened to be passing by, and that, it was just a coincidence. In the
first place, what can a mere merchant say to summon a High Monk,
and that doesn't make any sense……"

Qing did not push further by raising her voice, arguing whether it was a
lie or not.

To think the High Monk was just passing by.

No three-year-old child would believe such a lie, so there was no need to
argue about it.

The listening crowd would be even more incredulous.

Of course, in an official setting, if the High Monk claimed he was just
passing by and saw the assembled crowd, intending to subdue them,
no one could openly disbelieve him, even though they wouldn't believe
him. However, a mere Branch Manager did not have the authority to
force commoners to believe him.

"Still, you said that the Jangheung Trading Company was ordered to
profit viciously by selling grain at fifty times the price in a flood-stricken
village. Did that order come down or not?"

"No, it's not like that! Never."

"Then did the Branch Manager make that decision?"

"Oh my, how could a mere Branch Manager have such authority?"

"Oh my. Branch Manager. You seem to think I'm very easy and funny
since I'm speaking to you gently with a nice expression? You said no
orders came down from above. And you said the Branch Manager has
no authority. Then where did the cause for the grain price to be fifty
times come from?"

"That is……"

The Branch Manager was at a loss for words, stuttering.

In fact, this was like a Divine Art of merchants.

I have no authority, so inquire with the headquarters.

You want to inquire with the headquarters? But the headquarters won't
know anything either.

Then where should I inquire?

I don't know either. It's up to you to find out.

Even if a problem arises, there is no one responsible, so no one takes
responsibility.

It's the completion of a world where only merchants do not get hurt.

If this happens, even if the customer is furious, they can't do anything
since an individual can't deal with a trading company.

Moreover, if people gathered, it would be an attempt at treason,
forbidden by national law, and they would likely be hanged.

However, if they ignored all that and rushed in, what could a mere
branch of a trading company do?

"Ah! My mistake. I'm sorry. I seem to have misunderstood something
firmly. After all, I spoke as if the Jangheung Trading Company intended
to exploit the situation by raising grain prices. Surely. That can't be
the case, right?"

"That's, well, that is……"

The Branch Manager was sweating profusely.

If he agreed, someone would have to take responsibility, and if he
disagreed, he would have to lower the price of grain.

"Now. I've come to buy grain. All the quantity you have. How much are
you looki, no, I mean, how much are you selling it for?"

"W-Well, now is not the time to sell grain. It's not for sale, not for sale."

"Ah. So at a time when many people in the city are without food due to
the flood, you have mountains of grain piled up, but you won't sell?
Why?"

"That's a matter of the trading company, so it's not something I can
tell outsiders……"

What's with the 'outsiders' now?

Qing let out a snort.

"Ah. So the Jangheung Trading Company is going to hold onto all the
grain and watch people starve to death? Was this also a decision from
the headquarters? To just watch everyone starve to death? Wow. Did
you all hear that? They're just going to watch you all starve to death."

At this, the crowd's expressions began to turn murderous.

"N-No! How could that possibly be the case!?"

"Then is it the Branch Manager's decision? To cook and eat delicious
meals alone while everyone else is starving to death?"

"I-I don't have the authority to……"

Qing cocked her head.

"Branch Manager? Then what authority do you have? If the Branch
Manager has no authority over the branch, is it just a dream job where
you sit around and receive a monthly salary?"

"I can't teach you the internal regulations of the trading compa……"

"By the way. If we were to borrow some grain from the grain warehouse,
would the Branch Manager have the authority to stop us?"

"T-That's no different from robbery!"

"Robbery? I said we'd borrow it. Can't you hear? Of course, I can't say
when we'll pay it back, and I can't give you a promissory note either."

"What's the difference between that and robbery!"

"Hmm, fine, let's say it's robbery? So what can the Branch Manager do
about it? Are you going to stop us with your body?"

"That's a crime and illegal! The national law clearly exists, so how can
you say such outrageous things!"

"Ah. Never mind. Everyone! They're saying they'll just keep the grain
until it rots instead of selling it, so shouldn't someone else just eat it
instead? I, Ximen Qing, will take full responsibility! Let's go borrow
some grain!"

One must know when to stop.

If they didn't like this and didn't like that, making all sorts of excuses
and trying not to lose even a bit, then what the fuck was the point of
these bastards?

Moreover, the Jangheung Trading Company was responsible for the
flood control construction, so whether the cause of the flood was poor
design, shoddy construction, or inadequate management of the
sluice gates, they should take at least minimal responsibility, shouldn't
they?

If they were determined to make a fortune from the grain, then they
would have to face the iron fist of wrath.

"Wait! You can't do this, please!"

The Branch Manager ran out barefoot and blocked Qing's path.

Qing smiled brightly and said.

"Branch Manager? Shall we talk a bit?"

Since the crowd was on her side, she could achieve all her goals. But
since he said to talk separately, there must be something he was
hoping for.

For instance, demanding gold and silver in private and releasing the
grain.

Or perhaps asking for a connection to the Jangheung Trading Company.

Not far off, the head of the trading company was on intimate terms with
the Provincial Governor of Shaanxi as sworn brothers, so if he wanted
to connect to the government, wouldn't it be a direct line?

People only see what they want to see, so that was what the merchant
thought.

However, the first words smashed his expectations.

"How about the grain? I can give you up to double the market price."

"Great Hero, please consider my situation. At least ten times the
original price is needed to make a profit."

"You're going to profit ten times over from people who have become
beggars due to the flood?"

"If it's ten times, to that extent……"

At this, Qing responded with a monologue.

"That's strange. It doesn't sound like something a human would say. Is
there a demon or a monster sitting in front of me? I guess I have no
choice but to slay the demon as a member of the Daoist Sect."

"Two times, I'll give it to you for two times the price……"

"Alright. Geoltaran, check the quantity and write up the contract, um. I
don't know much about this, so Geoltaran, you handle it well."

"Yes, Young Miss. Leave it to me. Not even a single grain will be
missed."

"Yep. Yep. It's always easier to have someone smart to do the work."

"Sniff. What an honor, such an honor! A blessing for three, no, a
thousand, ten thousand generations. How could such an undeserved……"

Geoltaran suddenly started to tear up and then got up, bowing deeply.

After all, the Heavenly Demon, who had returned to the mortal realm,
had personally praised him. The emotion was like a miracle of cosmic
proportions, as if the heavens and the earth had been turned upside
down.

The Demonic Cult's agents, who were active outside the sect, were
fanatics who had undergone brainwashing akin to torture since
childhood.

At this, the Branch Manager's expression turned to one of disgust.

Could she perhaps be a noblewoman of great status?

That would explain why the High Monk had suddenly retreated. After
all, when the government backed down, it was either because of a
peerless Master or a status more esteemed than their own.

"By the way. I heard that the Jangheung Trading Company handled the
flood control construction. I'd like to meet the person in charge."

"About that……"

"If you say you don't know again, I'm really going to get angry, okay?
You want to die? Do you want to see my hungry Moonlight Sword drink
blood? Ah. It wouldn't be able to see anything when it's dead, huh?"

Now she was resorting to outright threats.

However, in the office, there was only the Branch Manager, Qing, and
one fanatic as a bonus.

Where could the Branch Manager complain?

"Well, that's not it. It's just that there isn't exactly a person in charge
of the construction."

"What? The river flooded, but there's no one in charge? Does that make
sense?"

"Originally, the flood control official should manage and supervise,
thus taking responsibility and determining any negligence, but there is
no such official. They only exist by name."

Hmm. The Zhongyuan is truly a mess, isn't it?

Qing thought that Zhongyuan was messed up as she changed the
question.

"Hmm. Then, who profited the most from the flood control
construction? Or achieved merits? Anyway, there must be someone
who was promoted because they did well due to the flood control,
right? Who is it?"

"That's……"

The Branch Manager glanced around again.

At this, Qing quietly placed her beautiful hand on the sword hilt instead
of urging him.

"The one who secured the construction contract and oversaw the work
was the daughter of our Clan Lord, Miss Jun Samwol. Due to that
achievement, she was put in charge of the distribution network in
Henan……"

"No, see, that's what I'm saying. If she secured the contract and
oversaw the work, then who else would be in charge but her?"

"The responsibility is a different matter, though……"

The word that merchants hated the most was responsibility.

Responsibility included things like refunds and after-sales service,
which merchants hated the most.

Therefore, trading companies tried not to have anyone in charge by
vaguely writing the subject of the contract, seating a figurehead,
complicating the departments, and organizing the work similarly to
create an infinite rotation of passing responsibility.

"Hmph. Whatever. And then, tell me everyone involved in the
construction. Who was the carpenter, who was the head carpenter?
Who procured the materials?"

"I don't know that. I'm not hiding anything, but I really don't know.
Such large projects are handled by the headquarters, so how would a
Branch Manager stuck in the countryside like me know anything?"

"What do you know then? Were all the construction workers brought in
from other regions? Weren't the wages obviously skimmed off in the
middle?"

Having worked as a construction worker before becoming a factory
worker in her hometown, Qing knew this area's workings just as well as
Zhongyuan.

Saying they skimmed off wages was putting it nicely. It was just a labor
brokerage fee, so it wasn't entirely unreasonable.

Of course, it depended on how much they skimmed off.

"Well, that's true, but wouldn't all the major positions have been filled
by people sent from the headquarters? I just handled the brokerage and
took a small cut. Um, if you want the list of workers, it should be
somewhere. If you wish, I can find it for you right away."

It seemed he really didn't know much about the construction.

After all, his Evil Karma was just barely at a level where it felt a bit off
to kill him right away.

And it wasn't likely that he was originally a good person, but became
like this after being hit with a Evil Karma bomb.

If anything, it was a miracle he was still under 100.

If his Evil Karma had been over 300 when I first met him, I wouldn't
have even talked to him.

I would have just led the crowd to properly loot everything.

At this, Qing let out a deep sigh and spoke.

"What are you doing? Go find it quickly."