\chapter{Drifting Off Course (2)}
No need for elaborate explanations in ecology or anthropology; people originally lived by the river.

Surprisingly, this is because people can't live without water!

Therefore, most cities in Zhongyuan were built alongside rivers.

If it was a large river, the city would hug its side; if it was a small river, the city would straddle it.

However, small-scale villages were located exceptionally on the ambiguous ridges of mountain slopes. This was a characteristic of fully fortified clan villages, prepared for the traditional culture of Zhongyuan, which was raiding neighboring villages.

If it was not such a closed-off neighborhood, they were usually located by the river.

Meanwhile, above Mount Gan flowed the famous Yellow River, one of the three great rivers of Zhongyuan.

And below Mount Gan flowed the Luohe River, a tributary of the Yellow River.

Incidentally, the name of the Yellow River means 'Yellow-colored River', but the character '河' itself means the Yellow River.

The Yellow River was the cradle of civilization, and when this terribly barbaric script was first created, the only river was the Yellow River.

Therefore, saying Yellow River would be like saying 'Yellow-colored Yellow River', which further translates to 'Yellow-colored (黃) Yellow (黃) River (河) River (河)'. It ends up being quite ungrammatical.

Yellow-colored Yellow-colored River River.

And the character '洛' in Luohe River uses the character for the Yellow River. When translated, it becomes 'Yellow-colored Yellow-colored River (洛) Yellow-colored River (河) River (河)'.

Yellow-colored Yellow-colored River Yellow-colored River River.

It was a river with a very peculiar name.

Thus, when Qing came down from the mountain-

Since the land was devastated by the flood, she had to get off the carriage halfway and push the wheels through the mud to barely reach Luoning City.

However, the name of the city, Luoning, meant 'wishing for the peace of the Luohe River'.

As could be inferred from its name, it meant that the city would be utterly destroyed if the Luohe River overflowed.

And the Luohe River did overflow.

"Ah……."

Qing, with mud caked below her knees and splattering everywhere, was greeted by the tragic sight of a city already in ruins.

The city walls close to the river had collapsed, and the civic-minded people of Zhongyuan were busy clearing the debris.

Of course, this debris would be carefully taken and used to repair their own houses, thus achieving perfect recycling without any waste.

Since the flood had also destroyed the gate tower that continued from the city walls, even the function of the city gate was no longer intact.

There were not even guards protecting the gate, so they just drove the horses through, entering the city. From the main road, to the left where it met the river, almost no obstacles remained to block the view.

The right side wasn't much better; people were busy pumping out muddy water from the buildings that were still somewhat intact.

Even then, those who were busy were considered lucky. Most were just sitting there blankly with a look of utter despair, as could be seen everywhere.

Qing's heart felt heavy seeing this.

In fact, Qing knew that floods were a regular occurrence in Zhongyuan.

Old cities often had relics and basements emerge when digging into the ground, as they were repeatedly buried by floods and rebuilt upon.

However, knowing about it and actually confirming the devastation were markedly different.

Then her thoughts drifted to the gold piled up in the carriage.

Yeah. What else would I use gold for?

And what could be more satisfying than giving to others with someone else's money?

But… even with such a decision, she felt at a loss.

I have the gold, but what should I do? How?

Of course, Qing was someone who would ask if she didn't know.

It was one of her few strengths.

So Qing tried to do just that.

"Young Lady Seol. Perhaps… Haaa……. Never mind."

You should ask the right person the right question.

Moreover, what would a girl who lived in a place with nothing but ice know about floods?

For a change, Qing tried to think for herself.

Hmm. To start with, wouldn't there be big trading companies or grain merchants in the city? For now, give them the gold and distribute food with the available supplies. For reconstruction, pay an advance to large firms to take on the construction work.

Ah. Right.

There should be an Orthodox Faction's martial arts school here, and surely the locals would be more knowledgeable.

Thus, Qing drove the carriage towards the Orthodox Faction in Luoning, umm. The name itself was very local.

To be precise, the horse knew the way and would slow down slightly at intersections, and Qing would just pull the reins to set the direction.

As they slowly (because she didn't know how to drive fast) made their way, they came upon a large open space where a crowd of people had gathered.

From the coachman's seat, beyond the heads packed tightly together, she saw a boy hanging by his neck from a tree.

He seemed to be standing on something, barely keeping his airway open.

Qing stood up from the coachman's seat to get a better view and saw that the boy was standing on the shoulders of a man, barely surviving.

The man and the boy looked exactly alike, clearly father and son.

It was a miserable sight to see a son barely clinging to life, hanging by his neck while standing on his father's shoulders.

People were throwing mud and stones at the father supporting his son. Despite being hit, the man was desperately trying to maintain his balance to support his son.

Qing saw people a bit differently.

She didn't see them three-dimensionally. Rather, she could see the karma they possessed as a number, allowing her to roughly gauge their actions without being swayed by first impressions.

The man and the boy.

Evil Karma 21, Righteous Karma 1.

They seemed like ordinary people.

But still, you never know.

Qing jumped lightly down from the carriage. Seol Riri tried to get off as well, clumsily grabbing her arm, leaning her torso, and turning her body, but…

"Ah. Young Lady Seol, just stay here. Why follow when you're not well? Just sit and rest."

"Yes."

To Qing, it seemed like Seol Riri's entire outer skin was bruised black and blue, so her muscles wouldn't be in good shape either.

So, she was clumsy, but it looked like she was trying very hard not to show that she was in pain. She looked a bit pitiful.

But that was all.

Qing cut off her concern and placed her hand on the shoulder of a bystander.

"Hey. What's going on here? Why is that person hanging there?"

"Hey, why are you putting your hands on someone else's shoulder, wa-."

The man, who had brusquely shaken off her hand, turned his head and was struck by the accident of encountering Qing's harmful beauty up close.

Qing's beauty was harmful.

It made the heart race, causing blood pressure to rise, which in turn could lead to various side effects.

Her beauty was not only physically harmful but also mentally very, very detrimental. Once seen, the mind would become dazed, and if one was married, they would be cursed to return home and see a dried fish occupying their bedroom.

"What's going on?"

"Ahem. It's said that that guy designed the flood control system for the Luohe River."

The man cleared his throat and spoke with a low voice.

For some reason, men thought lowering their voice made them sound cool.

"And?"

"He boasted that it would last a thousand years, but what do you know? The embankments and levees all burst after just one heavy rain. If it hadn't been built at all, the water might have just overflowed a bit, but it's all because of that guy……"

It seemed that since last autumn, there had been a flood control project to rebuild the floodgates and embankments of the Luohe River.

However, that was the root of the problem.

If it hadn't been built at all, even if it rained heavily, the river would have just overflowed as usual.

But since they built a floodgate to block the water, the water level rose beyond its limit when it rained.

Thus, the floodgate burst, and water rushed in all at once, breaking the embankment in one go.

Therefore, a massive disaster struck the city, and even the collapsed city walls were a testament to the immense calamity.

"Hmm. So the one who designed it is the father, right?"

"That's right."

Just one point of Righteous Karma.

But even one point proved that the child was innocent, so she couldn't just let him die.

"Hmm. Could you move aside?"

"Huh?"

Though she said to move aside, Qing's arm was already moving, effortlessly creating a path as if a bull was pushing through.

Thus, as Qing entered the center of the open space, the projectiles that had been flying stopped at once due to her beauty.

Then, Qing jumped up and cut the rope, catching the boy and landing lightly.

"Everyone, I understand your anger, but this child has done nothing wrong, hasn't he? If there's a crime, there should be punishment, but the child has only had the misfortune of having the wrong father."

"Don't make me laugh! If the father is at fault, shouldn't the son pay the price as well!"

Someone shouted.

Quickly, murmurs of agreement spread.

Qing stomped her foot on the ground.

Everyone felt the vibration through their feet, and the murmuring stopped again.

It was as if the ground rumbled with just a stomp of her foot.

The fairy-like woman seemed even more divine now.

Of course, Qing had no intention of defending the father as well.

The flood control project was a critical matter involving people's lives. If there was a flaw, whether intentional or not, he was responsible for the disaster.

The flood victims had the right to throw stones, so whether the man was stoned or set on fire was none of her concern.

But still, the child seemed innocent.

If it were the young lord from the bandit's place, with Evil Karma stacked up to 300, Qing would have happily thrown stones with them. However, one point of Righteous Karma, even if just one, was still Righteous Karma.

The human heart was cunning; the same words could elicit different reactions depending on the speaker's beauty.

When a heavenly, fairy-like beauty spoke, people cleared their throats and didn't particularly object.

Hmm. But.

Qing looked at the flood control designer.

The father, who had been desperately supporting his son, now looked completely relieved, his gaze filled with infinite gratitude towards Qing.

Evil Karma 21.

Qing was gradually understanding, even if she couldn't quite explain, the concept of Righteous and Evil Karma.

Righteous and Evil Karma had no intention.

It merely assigned a score based on the outcome of an individual's actions. Whether the flood control designer was intentionally negligent, made some calculation error, or simply didn't expect such heavy rain, he was assigned Evil Karma corresponding to the pain and sorrow caused by this disaster.

And yet, only 21 points of Evil Karma.

Even after receiving a massive amount of Evil Karma, this score meant he must have been a very good and upright person.

It was then.

"F-Fairy! Please save my dad too! My dad did nothing wrong!"

The boy, who had been gasping for breath, shouted.

As Qing looked at the boy, he continued to yell.

"This much water could have been easily withstood by the design! If the construction had been done properly, it wouldn't have burst! It's all because the construction wasn't done properly!"

Hmm. This is a new perspective.

Qing was about to examine the man again when-

"What nonsense is that child spouting! He's just trying to defend his father. Even so, how can you say that boy has no sin! He should be hanged again immediately!"

"Ah, seriously."

Qing drew her sword and raised it high, emitting a beautiful, sparkling Sword Force.

It was a pretty starlight that made everyone shut up.

Sword Force was something that even those who didn't know martial arts could recognize. Moreover, the sharpness it exuded made ordinary people's hearts drop with a chilling sensation.

After silencing the crowd with the display of Sword Force, Qing examined the man again.

Evil Karma 21.

If the design was correct and he wasn't involved in the construction, would he have received Evil Karma from this disaster, or not?

The flood control designer seemed to interpret Qing's gaze differently.

"……It's true."

"What? The construction was faulty?"

"I have always dreamed of leaving my name in history through flood control, like Dujiangyan1. Even if it rained for thirty days and nights, like yesterday's rain, the design was meant to withstand it, but."

"But it burst."

"The floodgates should have been opened little by little as the water level rose, but either the operation was unskilled, or the construction was shoddy from the start."

"Hmm. You're upset, but why are you only saying this now?"

"I did say it, but then they dragged my son out, so……"

"Lies! It's all lies! That guy is just trying to shift the blame to innocent workers-"

Look here. Sparkle, sparkle again.

Qing's ability to wield Sword Force was truly awe-inspiring.

Wow. With just one display, everyone shuts up and becomes quiet.

But that aside.

Qing pointed her sword in the direction of the voice.

"Just now? Who spoke? You've been heckling since earlier. If you have something to say, come out and say it. Why hide? Would you like to come out here?"