\chapter{Drifting Off Course (1)}

For several days, it had been raining continuously, and it was a heavy downpour at that. So, it wouldn't be strange if a part of the mountain, where the ground was soft, had collapsed.

Fortunately, the sound came from a distance, but that didn't mean they weren't anxious.

Is it okay here?

It won't just collapse, will it?

But there was nothing they could do about it.

On a primitive ancient night, there was no light source other than the moonlight, leaving everything pitch black.

The only portable lights were torches or lanterns, but on a night of heavy rain, even those were utterly useless.

Therefore, they couldn't go down the mountain in the middle of the night, and even if they did, there was no guarantee that it would be safe.

If anything, the mountaintop might be safer.

At the very least, they wouldn't have built a hideout in a place that would collapse, right? Even if the bandits were ignorant, surely they had that much sense?

Having made her decision, Qing headed inside the stronghold.

It was a structure that could be called a giant roof.

A large fire was lit on one side under the roof without walls, clearly illuminating the entrance to the building.

After all, even bandits wouldn't sleep in a shelter with only a roof, using the ground as a bed.

If so, what would be the difference between bandits and barbarians?

Hm? They do seem like barbarians, though.

Anyway, the method to find the best room was obvious; just follow the hallway and look for the most lavish door.

Originally, those without authority were obsessed with authority. So, at the end of the hallway, there was a large door decorated with gold and scarlet, with a lantern hanging beside it, screaming, 'I'm here, the boss's room.'

Since it wasn't her house and she wasn't a guest, Qing, whose hands were sealed by Seol Ri, kicked down the door with a powerful and precise motion.

As the door fell like a drawbridge, it revealed the interior.

And inside-

"Ugh. It smells like an old bachelor……"

Scorn was etched on Qing's unparalleled, most beautiful face under the heavens.

As soon as the door fell, a strong smell of an old bachelor hit her, almost making her lose her nose.

At least the bed looks nice.

It was wide, large, and high, clearly a luxurious and comfortable bed. However, the silk laid upon it…

Only the feeling that it was a high-quality item suitable for the bed remained. The color had turned yellow from the center to the edge of the bed, and upon closer inspection, it was clear that the source of this potent old bachelor smell was the bed and the carelessly discarded blanket.

Qing picked up the blanket and licked it open, and at that moment, a smell that was similar to a night-blooming lower but much more fishy, damp, and musty, hit her again.

Ugh, it's so dirty. Disgusting.

Is this a blanket or a rag?

After carefully laying Seol Ri down, Qing picked up the blanket and wrapped Seol Ri in it.

The kid had turned into such a wreck, and she was completely soaked from the rain, so she had to maintain her body temperature.

Seol Ri turned her head with great effort and followed Qing with those large eyes.

"It…… smells……."

"What, does it smell a little? What's the big deal? It's dirty, but it's still a blanket. It's not like they pissed on it or anything. It's just the sweat and saliva of the bandit leader, heavily fermented. That's all."

Qing's expression was bitter as she spoke.

It was no lie. Ugh, just saying it out loud makes it even more creepy and disgusting.

Seol Ri's eyes widened, and she tried to move her body, but she groaned in pain and frowned.

"See? You're not well. Just wait here. I'll change and come back, I mean, I'll bring a change of clothes."

She wanted to get out of this smelly space as soon as possible, to the point where she was even stumbling over her words.

As she was heading back to the carriage, Qing suddenly looked outside.

"This damn rain is really pouring down."

It was her fifth year in Wulin, and this was the first time she had seen such an endless downpour.

Well, after five years, it was about time to experience heavy rain.

But is that young master still alive?

Since the clothes were already wet, Qing stepped out from under the roof towards the puddle where she had roughly thrown him.

The heavy raindrops made a refreshing sound as they struck her face.

There were three corpses with their limbs missing, and in the middle lay the young master, frothing blood.

His Evil Karma was a little over 300. Wow, he's still alive.

He must have a tenacious will to live since he's a bad guy.

However, even if the best physician in the world were here right now, he was beyond saving.

If she thought he could be saved, she wouldn't have thrown him there in the first place. It wasn't that she was just leaving him to chance, intending to kill him out of a change of heart if he survived.

Well. How insignificant.

Losing interest, Qing turned around.

After taking clothes from the carriage and returning to the stronghold, Qing kicked down every door she saw, searching the interior.

Even if the bed was luxurious, she couldn't sleep there because of the smell. It wasn't just any smell, but an old bachelor smell that seemed to contaminate her lungs.

But the boss's room was like that, so what could be expected from the other rooms?

If anything, the boss's room was better. The rooms used by several unwashed men were even worse, if that was possible. Ugh.

Then she found the kitchen and looked through the ingredients. Luckily, it seemed like she could have a hearty breakfast. Hmm? What's this?

There was another door inside the ingredient storage.

It was firmly locked, so Qing, once again imitating a barbarian, kicked it open-

"Ouch."

Usually, when kicking something, the less damage the target took, the more shock the body received.

Conversely, if the target was destroyed, the impact on the body was reduced. So, Qing frowned at the throbbing pain in her ankle.

What's this? Is it made of iron or something?

Qing saw a padlock as big as two fists on the door and her eyes lit up.

Oh ho. There must be something good in here, right? A treasure vault?

The padlock was sturdy, but the iron ring it was attached to was not. Qing twisted the padlock, and the iron ring twisted and broke off.

Thus, a staircase leading to the basement was revealed. After lighting a lantern, she went down. Wow, seriously.

In the small storage, a yellowish glow was reflected, glittering. Wow, gold!

Qing picked up a gold ingot, called a 'gold lump'.

Originally, gold was a heavy item for its volume, so its precious weight was felt heavily in her hand.

Ah. So that's why there were two Transcendent Realm.

Roughly counting, there were over 40 gold lumps. It was an immense amount of money that needed to be guarded by two Transcendent Realm.

Wow. These bastards.

They've amassed this much gold from banditry?

Just how much did they plunder?

Qing regretted it belatedly.

I shouldn't have killed them so cleanly.

She thought that banditry was just about making a living by robbing and stealing, but…

This was a full-blown criminal enterprise. Absolute bastards, these were.

It was already too late to do anything about it.

Qing was someone who could sleep on the streets if she had to, but the thought of sleeping on a bed stained with the sweat, saliva, and, ugh, disgusting, of those black-clad men made her feel sick.

She decided to just put the sick Seol Ri there and thoroughly raid the bandit's lair since she wasn't particularly tired and didn't need to sleep right away.

When she returned to the smell room, Seol-i was snoring softly and cutely again.

Now that she look at it, it seems like it's not because of a cold, but because she's a bit of a snorer.

"Young Lady Xue, change your clothes and go to bed. You'll catch a cold again."

"Yes…"

Shee was the type of person who would answer if you talked to her while she was sleeping, and she answered while snoring loudly.

Qing unwrapped the blanket wrapped around Xue Iri, and, ugh, the smell…

The wet, clammy clothes were hard to take off. The child is lying limp and half asleep. Even if Qing smacked her, she won't even say "yes" but is just completely unconscious.

When it's hard to breathe because of the smell, I wonder why I'm trying to take off her wet clothes, wipe her body with a damp cloth, and then change her into dry clothes at this time of night.

It's not even a kid, really. It's useless.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The morning after Qing had thoroughly searched the stronghold, she found not only gold ingots but also a decent amount of money, weapons to be sold as scrap metal, and several Secret Manuals.

However, among them, only two Blue ones appeared in the Martial Arts Window. The others, despite having grand names like Great Strength Bloodfist Method, Wild Dragon Dao Technique, and Eight Section Heavenly Staff, did not respond even when touched, unfolded, and examined.

It meant they were not proper Secret Manuals.

Well, what could one expect from bandits? It was unlikely they would teach their subordinates good martial arts.

They probably omitted key parts or twisted the Qi circulation to cause defects.

She had loaded all the gold ingots into the carriage's cargo compartment and piled weapons on top for camouflage.

Since it was still the middle of the night, Qing covered herself with a blanket in the carriage and waited.

She might have dozed off, or maybe not.

Then it was morning.

When morning came, the rain had reduced to a drizzle, and although the thick, dark clouds still covered the sky, it felt like it had brightened up a bit.

Ah. There was a landslide last night, wasn't there?

Qing, wearing a bamboo hat, jumped onto the roof of the lookout post, which she hadn't even known existed last night, and surveyed the area below the mountain.

Ah. It wasn't a landslide.

It seemed like a strategic decision to cut down trees to have a clear view from the lookout post.

Thus, the mountain path leading up was clearly visible, and the view extended to the ridge below. Amidst the morning mist, a devastating scene at the foot of the mountain was revealed.

It wasn't a landslide but a flood.

The tributary of the Yellow River flowing south of Mount Gam had overflowed.

It was a complete mess, with a thick band of yellowish mud and fallen trees stretching from east to west as far as the eye could see.

If I had been down there……

Then she realized that if the coachman hadn't brought her to the stronghold, she would have been swept away.

The road ran alongside the Nakha River below Mount Gam, and now there wasn't a trace of it to be found.

Coachman. You had such great foresight.

And here I was, not knowing…….

Since he did a good deed before dying, maybe the Grim Reaper will reduce his sentence by a day or so.. 

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing wasn't good at cooking, but she's not bad at it either.

In fact, Qing was not that picky about food.

Rather than being picky, she's the type that has no particular way of eating, so no matter what she ate, she'd say it's delicious and worth eating and just shove it in.

And this type has a hard time being good at cooking.

But Qing also remembered the taste of the various ingredients she had eaten in an amazing way.

As a result, even dishes that were roughly stir-fried in an iron pan with oil came out edible.

She put dried meat in a pot, roughly chopped up some herbs to get rid of the gamey smell, poured in rice and barley water all at once, boiled it vigorously, and made a large pot of porridge.

When she returned to the smelly room, Xue Iri was snoring softly with a cute, low sound.

Now that she thought about it, it wasn't because of a stuffy nose, but it seemed like she had a habit of snoring lightly in her sleep.

"Young Lady Seol? Wake up and eat breakfast. We should get going soon. I made some congee."

"Congee……"

At the mention of congee, Seol Ri's eyes shot open, and she tried to get up, only to groan, "Ugh," and collapse back onto the bed.

"Young Lady Seol? Are you okay?"

"Yes."

She kept saying she was okay, but…

Yesterday, when she was wiping her down, she saw that her entire body was covered in dark bruises.

Her back, shoulders, arms, and the outside of her legs were so bruised that it was hard to find any unblemished skin. However, the inside of her torso, arms, and legs were white and fair.

It meant that she had been beaten while curled up in a ball, unable to fight back.

So, it was no wonder her entire body was aching.

No, a martial artist should counterattack.

If she curled up like an armadillo, she was bound to be beaten until death, wasn't she?

That's why she was dragged around by her hair.

Her skills are poor and her attitude is all wrong.

Honestly, just her face, ah, her face…….

"Can't you stand? Do you want me to carry you?"

"No."

Seol Ri said this and then, very slowly and laboriously, like an old person about to die, managed to get up by holding onto various things.

Then, sticking close to the wall and using her hands to support herself, she managed to take one step at a time, following her.

Since Qing had no intention of carrying someone who refused, she simply led the way slowly.

And so, they had a hearty breakfast.

And then, they had to leave.

"Can you drive a carriage?"

"I'll do it."

"No, if we're not careful, we'll end up stuck somewhere. It's not about whether you'll do it or not. Can you do it or not?"

Seol Ri bit her lip.

Her will was commendable, but what could a girl who was trembling while eating congee do with a carriage?

As Qing's eyes narrowed, Seol Ri offered another answer.

"I'll tell you how."

"What? How to drive a carriage?"

"Yes."

"Can you learn that in one go just by being told?"

"It's easy."

Qing didn't like living people, but she did like the flesh and bones left behind after death.

As such, there was no way she could stay in a stronghold that had turned into a mess of corpses.

And so, Qing's first experience as a coachman!

Surprisingly, it was easy.

And for a good reason. Horses had eyes too.

Moreover, horses were very timid creatures.

Since they were animals with eyes and a lot of fear, they avoided obstacles on their own. If they thought something was dangerous, they would refuse to go, no matter what.

The reason why warhorses were expensive was that it was incredibly difficult to train such timid animals to charge at enemies.

Ah shit. So being a coachman was a really easy job, huh?

Of course, it was an easy job.

Being a coachman was considered one of the five most menial jobs in the world, partially because it was so easy that anyone could do it.

Of course, driving at high speeds or navigating rough terrain while maintaining a comfortable ride required great skill, but if the goal was just to pull the carriage, anyone could do it just by holding the reins, as the horse would do everything else.

Horses preferred well-maintained, solid roads over forests or uneven terrain.

Although the road was slippery and downhill…

Since the stronghold had paved a winding, gentle slope for carriages to ascend and descend, it was manageable to navigate, albeit with some difficulty.

The wheels often got stuck in the mud.

But here they had the superhuman, the transcendent, the peerless Qing. She was also known as Yeo Hangwoo, as well as the Human Crane, Ximen Qing.

Whenever the carriage got stuck, she would push it out and then return to the coachman's seat, watching the swaying horse's ass before getting stuck again with a thud.

It turned out that horses were quite intelligent.

When the carriage got stuck, it would immediately stop, turn its head, and look at Qing.

As if to say, 'What are you doing? Not getting the carriage out?'

And then, a simmering rage would begin to rise.

\textit{No, what the hell is this hardship?}

\textit{Xue Iri, that thing, her only redeeming quality was her ability to drive a carriage, but now I'm doing even that.}