\chapter{Drifting Off Course (5)}

As Qing gracefully leaped up with her anti-gravity gait and landed softly with a tap!, exclamations erupted from all around.

Of course, ordinary people's standards were quite low, so it wasn't that they recognized the peerless footwork that allowed her to slowly float up and down.

However, they had witnessed a movement so extraordinary, akin to that of a deity, that people started to make hand seals, calling out to the Heavenly Maiden or Fairy.

As Qing confidently stepped forward, the crowd parted to the left and right, creating a path.

It wasn't quite comparable to someone parting the sea, but it was a rather impressive scene nonetheless.

As Qing walked proudly with a tap, tap, tap, people followed her, seemingly entranced, maintaining a distance.

Seeing this, Geoltaran's eyes turned red, and tears welled up inside.

The Heavenly Demon Supreme is leading the people!

It is not with tyranny but with virtue and kindness that she lays the foundation for conquering Zhongyuan. Ah, only the brightest future awaits the Heavenly Demon Divine Cult!

However… Could she not exude a bit more solemn dignity as she walks…….

The only reason why Geoltaran didn't burst into tears of emotion was because of that obscene and wicked sway of her hips, naturally stealing a man's soul as she walked.

At any rate, Geoltaran quickly snapped out of it, pushed through the crowd, caught up to Qing, occupied a position one step behind her to the right, and clasped his hands in a respectful posture.

It was as if he felt like he had become the right-hand man of the Heavenly Demon Supreme, continuing to soar in a sea of emotion and joy. It was to such an extent that he wondered if he had already died and arrived in paradise. Was this a dream or reality?

"Geoltaran. Which trading company in this town has the most grain?"

"That would be the Jangheung Company, of course."

The Jangheung Company, huh.

Wasn't that the company that took on the construction project?

I should pay them a visit, but not now.

The most delicious part should always be saved for the last bite. That's the rational way of intelligent people who know how to enjoy taste.

"Let's go there later. Who's next?"

"Then it would be the Nakryeong Company, without a doubt."

"Good. Let's go there. Where is it?"

"About that……"

Then, Geoltaran hesitated, unable to speak.

"What? Why?"

"You came the other way. It's behind us, back there."

Ah shit, I got the direction wrong.

It was hard to turn around when the crowd was following, and she couldn't just say, 'Ah, this isn't the right mountain,' and turn back after having taken the lead so confidently.

"Ah shit. It would look bad if I turned back now. What's ahead in this direction?"

"The fourth large gate up ahead is the Daewan Company."

"Good."

Thus, Qing headed for the gates of the Daewan Company.

Normally, the streets of any city's merchant district had a solid foundation and were very wide, since many carriages traveled them.

It was a wall of people, marching to fill that wide road that could easily accommodate six freight carriages.

As such a wall approached, the gatekeepers of the merchant district's estates stood with weak knees and trembling legs.

The gatekeepers of the three estates that Qing and the crowd passed by sighed in relief, while the gatekeepers of the Daewan Company prayed to Buddha, the Jade Emperor, the Heavenly God, and all other deities for the crowd to just pass by.

However, humans must save themselves.

No matter how divine, gods do not save humans.

"Greetings."

"Y-Yes!"

"I am a woman called Ximen Qing. I have something to say to the owner of the Daewan Company, yes. I have come to deliver good words."

"Uh, did you make a prior appointment……"

"Oh dear, I was in a hurry. But it's an urgent matter that can't wait, and it will also be good words for the Head? The Branch Leader? The Guild Master? Anyway, could you let me in?"

"That is, that would be difficult."

At that, Qing smiled and said.

"Do you want to make things more difficult?"

"N-No, not at all."

As they say, there is no general who can stand against sheer numbers. In front of the crowd that filled the street, the gatekeepers were merely powerless individuals.

Thus, as the gates opened wide, Qing marched in proudly with a tap, tap, tap.

As the crowd followed her and filled the spacious estate of the company, a group of martial artists suddenly blocked Qing's path.

"Halt!"

"Yes."

Qing obediently stopped.

"This is the Daewan Company's place of business. Even if the situation in the city is not good-"

"I am called Ximen Qing. How may your distinguished self be called, Great Hero?"

"Ahem. I am the first disciple of the Yiga Sword School, called I Banjo. Young Lady Ximen, for what purpose have you come, leading so many people?"

It was common in Zhongyuan for trading companies to donate money to local martial arts schools and 'invite' their martial artists to stay and be hosted.

Of course, this was never a case of martial schools ordering their disciples to guard someone else's house. It was always a matter of accepting the kindness and staying as guests.

Naturally, this was mostly the case for Orthodox Factions.

Unorthodox Factions were seen as troublemakers and received no help even if they did donate money.

And if they were part of the Orthodox Faction, well…

"If you ask for what purpose I have come, I must first tell you the story of my participation in the Wulin Competition."

Qing suddenly started telling a story no one had asked for.

"Even with my humble skills, I won the Hidden Dragon Sparring Tournament, receiving the excessive title of Heavenly Flower Sword. I was on my way back to deliver this joyful news to my sect, you see?"

I Banjo muttered, Heavenly Flower Sword.

Whether it meant a flower of the heavens or the most beautiful under the sky, he thought that either way, it suited her well.

"As I was returning and entered the city, I saw that a great disaster had struck. So, this girl decided to use her personal wealth to start a relief effort. However, since all I have is gold and silver, I came to ask the Head to sell me some grain."

"Ahem. Y-You are doing good, good work."

"Yes. So, could you please not worry, Experts, and open the way for me?"

"Of course, of course. You are doing good work."

For martial artists of the Orthodox Faction, reputation was as important as their life.

Of course, they were fiercely competitive when it came to reputation, so it was possible to refute such a shallow trick.

But it was the winner of the Hidden Dragon Sparring Tournament.

The strongest among the Rising Stars and the new star acknowledged by the Wulin Alliance.

The grand title of Heavenly Flower Sword exuded the dignity and authority of very high-ranking people.

So there was no reason to make enemies here, and no reason to stop someone from carrying out relief efforts.

In fact, I Banjo even added to that.

"Since you have set such a great intention, our Yiga Sword School will also join you. What are you all doing? In case there might be a disturbance, the disciples will protect the people."

Thus, he naturally took a position in front of the crowd, switching sides.

And so, Qing led the people forward again, making a firm and lively tap, tap, tap sound as she crossed the estate.

Then, in front of the main building…

"What is this commotion? Even if there was no prior appointment, how dare you force your way in like this?"

"I am called Ximen Qing. I know it is rude, but the matter is urgent, so I had no choice but to be impolite. Are you perhaps the head of this company?"

"Ahem. I am in charge of the general affairs of the Daewan Company."

"I have come to ask if you could sell me some grain, as I wish to carry out a relief effort with the gold and silver I have. May I see the Head?"

"I shall, I shall inquire."

The head of general affairs, who awkwardly responded because they had barged in unannounced, but she wasn't acting violently, disappeared into the building.

A moment later, he came out and said.

"The Head has given his permission. For now, could the Young Lady come inside and tal-"

"No. It's not just me, but all these people here who have come to make this request, haven't we? I know it's rude, but I would like to ask the Head to come to this place."

Qing cut off his words.

If she was going to negotiate one-on-one, she wouldn't have dragged everyone along in the first place.

If she just went in alone and showed off the sparkling Sword Force, they wouldn't dare to refuse such a polite request.

But if she did that, they might pretend not to know later, and if they played tricks, it would be a headache. Moreover, she had a mountain of grain to buy, so she couldn't visit each and every one of them to ask.

If she dragged everyone along and crushed the biggest company, the smaller ones would naturally follow.

"Th-That is difficult. After all, how can you bring so many people like this, it's no different from a threat, is it not?"

"A threat? I told you, it's a request."

"How is this a reque-"

"Ah. Suddenly, there's Sword Force all around. Head of General Affairs? Do you know about Sword Force? It's something you can use once you reach the Transcendent Realm."

Ordinary people in Zhongyuan did not have the insight to recognize the names of martial arts or their levels.

However, since they were well-versed in realms and terminology, and because the idiotic entertainment culture of Zhongyuan involved ranking martial artists, they naturally learned such common knowledge from an early age.

So, upon seeing the ominous starlight that sparkled, the Head of General Affairs' heart sank.

He didn't need to check whether it was real Sword Force or some trick to deceive him.

After all, the martial artists of the Yiga Sword School, to whom he had paid to guard the house, were standing right there, with their mouths agape, their eyes filled with admiration, awe, and respect as they looked at the woman's sword.

"When will the Head come? I'm frail, so I can't hold my sword for long. If my arm gets tired, I don't know where it will swing. You know?"

"No, that's really a threa-"

"Ah, that pillar! It's so thick, it makes me, as a swordsman, want to try cutting it! If I use Sword Force, it would obviously be cut, right?"

Now it was an outright threat.

At this, the Head of General Affairs shouted in fright.

"I will bring him! I will bring him right away!"

The Head of the Daewan Company was beaming with joy.

A crisis was an opportunity. And a time when a major disaster struck a city was an opportunity given by the heavens to multiply a merchant's wealth many times over.

Of course, he had been in a bad mood in the morning.

It was because of the news that some upstart merchant, the Taecheong Company or whatever, was spouting nonsense about distributing relief grain.

But that was only for a moment.

After all, how much grain could a new company that had just entered the area have procured?

When their warehouse ran out, that would be the end. And from then on, grain would be as valuable as gold.

Of course, the poor commoners wouldn't have money to buy grain.

But that wouldn't be a problem. They could just take out a loan, and if they had a daughter, they could bring her to pay it off. Or they could sell them as slaves or take their land deeds. At any rate, it would return as a huge profit.

The reason why a company suddenly grows large enough to establish branches after a major disaster was because of this.

But that joy only lasted until then.

They came in like a swarm of locusts, demanding to see the Head. What is going on? The Yiga Sword School bastards, what are they doing?!

"Even if I pay them in gold and silver, how can they act like this! Do they think the company will function properly!? Then who will pay the protection fees and make donations?!"

It wasn't like he could avoid paying the protection fees. After all, they were sword-wielding thugs, so how could he not pay when they demanded it?

The general manager thought so, but he wasn't so tactless as to say it out loud.

"You should call for the government's help!"

"Even if we do, how do we stop them right now? For now, the Head should step in to appease them or make a promise-"

"What kind of talk is that! If I go out there and say I can't sell, what will become of me?! I won't even be able to set foot in Nakreung!"

But he couldn't just not go out.

After all, so many people had gathered. If even one of them shouted, the crowd could instantly turn into a mob of bandits. This was just how people of Zhongyuan were.

So what could he do? He had to go out for now, and somehow buy some time or something.

"What did I do to deserve such a thing……."

The Head muttered.

If Qing had heard him, she would have had to hold herself back from giving him a noogie.