\chapter{Drifting Off Course (4)}

As they rode the carriage toward the commercial district, the devastated landscape gradually faded away, and a surprisingly intact cityscape unfolded.

"It's intact?"

"The Nakha River overflows every year, you see."

The Nakha River was straight for a tributary of the Yellow River, but the river's width was narrow, so floods occurred annually.

Therefore, it was common for commercial houses and martial arts schools to settle on the high ground along the continuous foothills. By this point, even the riverside shipping warehouses were emptied and moved to higher ground.

"But even so, they still did flood control construction?"

"That's not an easy task, you see."

The river was straight, but its width was narrow. Yet, it had a large water volume, so the river's current was fierce and rough.

Since the water volume was large, the river was deep, and the current was strong, it was a very difficult river for humans to manage.

"The government has finally loosened its purse strings and bestowed a great boon. But it has turned out like this. Hmm. In fact, whether that's truly a boon is something that needs to be pondered upon."

"What does that mean?"

"Such a large-scale flood control project would require an enormous amount of money, wouldn't it? There are already rumors that underhanded deals were rampant from the very selection of the project. And with the news that the Commissioner of Henan Province is being replaced, some say that he was trying to make a big profit before retiring. Of course, that's just hearsay, you know? There are also rumors that the Commissioner of Henan Province is an upright official, so who knows what people are really like."

The Imperial Family was stingy, but when they opened their purses, their generosity was akin to that of Buddha.

Gold and silver literally poured down in several carriages.

So, even after the officials took their share, there was still a substantial amount of money left.

The rest was handed over with the blueprints, with instructions to build accordingly. The construction was then left to the discretion of the commercial houses, who were to build well and pocket the remaining funds.

"Is that all? Isn't there anyone watching to make sure the construction is done properly?"

"Originally, the Flood Control Commissioner should monitor the construction and ensure it's done properly."

However, the Flood Control Commissioner was a very mysterious position that existed only in name.

It wasn't as if the government didn't send anyone for supervision, but they didn't understand the blueprints from the start and were ignorant of construction, so they couldn't tell even if they watched closely.

At best, those who only watched were considered highly upright officials. Most of these supervisors were said to be people with clairvoyance, capable of grasping how the construction was going even while receiving entertainment with women at high-class restaurants.

Of course, Geoltaran's words were all based on hearsay and rumors, so it was all a matter of 'believe it or not'.

When she heard that it was utter chaos, but also 'believe it or not', Qing thought, 'Surely it can't be that chaotic?'.

When the carriage arrived at the Naknyeong branch of the Taecheong Association, there were crowds of commoners in beggar-like states gathered.

"Oh, thank you. Thank you."

"No need for thanks. Next!"

Men with the word 'Qing' emblazoned on their chests were ladling out a scoop of grain to the lined-up commoners.

The strange thing was that the Righteous Karma of the men ladling out the grain was quite significant, one and all.

However, Qing watched as their Righteous Karma decreased by one point in real-time.

What's this? Did Gramps gather all the bad guys from somewhere to start a merchant association?

Hmm. Maybe they're escapees from the Demonic Cult or something?

Gramps' background might have led him to accept those kinds of people.

It seemed like they were already distributing relief, and seeing the Evil Karma decrease made Qing's mood a bit sour.

At times like this, she had very complicated thoughts, but the more she thought about it, the more it hurt her mental health, so Qing forcibly turned her gaze away.

Ah. Seeing Young Lady Seol's face is healing.

I think lookism is bad, but what can I do if seeing something pretty makes me feel pretty?

As Qing entered the association and got off the carriage, someone gasped in surprise.

Qing turned her head, and a man who had been sitting there dejectedly looked at her with an unbelievable expression.

What's wrong with him? Is he sick or something?

It seemed to be contagious, as another employee carrying sacks, who asked, "What's wrong, Yeo Danchi?", also dropped his load and bowed deeply, revealing the top of his head.

"Young Lady! Is it really Young Lady?!"

"Goodness, you're so beautiful!"

"It's an honor, an honor! The honor of three lifetimes, no, the honor of a thousand, ten thousand lifetimes!"

"Qing Dynasty! Qing Dynasty! Qing, Qing, Dynasty!"

Then, they rushed in droves. What's going on?

Qing just blinked her eyes at the extremely, fervently, and passionately warm welcome.

It was a welcome, but there should be a limit. After all, these were people who didn't know her face at all, yet they were bowing their heads in admiration, their eyes red with emotion.

"Hey, what's wrong with all of you?"

"W-Well, you see. Hey, you lot! Don't you have work to do? Even if you're overwhelmed by the sight of our Young Lady, you have to do your jobs properly, you know?"

"Ah. Apologies, apologies."

At Geoltaran's scolding, the association's employees hurriedly dispersed.

"Hehe, actually, all the employees here have received great kindness from Lord Choe. Since, uh, that's how it is… Well, that's that, so… They must be truly overwhelmed to see you, Young Lady."

Qing narrowed her eyes at this.

When did Gramps go around doing good deeds to have gathered such a group of people?

And their Evil Karma was quite unusual, at that.

Seems like they're really escapees from the Demonic Cult, huh?

He said it was the Seolga Merchant Association, but did he lead a mass exodus or something?

Qing had no idea that she was the Heavenly Demon.

To Qing, the Heavenly Demon was just an enemy she had already defeated, so only traces of the destroyed ego of the parasitic entity remained in a corner of her mind.

Only the Heaven-Shattering Demonic Qi, stuck in a corner of her dantian, was being beaten up and laughing.

Therefore, she also didn't know that Choi Leeong had allied with the Demonic Cult again, was trying to establish a foundation in Zhongyuan as a single sect, and was in the midst of burning with a very evil ambition to make Qing an eternal, supreme, and sacred idol.

After settling their things in the association…

However, Seol Yiri's condition seemed a bit unusual, as she was staggering and stumbling like a patient, which didn't look good at all.

"Young Lady Seol? Aren't you feeling well? You should get a diagnosis."

"No."

"I can get that you're saying 'no', but at least answer in order when I ask multiple questions. Are you saying you're okay, or that you don't need a diagnosis?"

"Okay. Yes. Yes."

In order, she's saying she understands.

She's fine and doesn't need a diagnosis, so yes. Yes.

It seemed Seol Yiri was obediently following her instructions.

Qing smiled and nodded.

At least she's obedient, which is good.

As Seol Yiri was told to rest and was sent to her room, Geoltaran, who had checked the gold loaded on the carriage, made a fuss.

"Oh my, where did you get so much gold? I can't fathom the extent of your abilities, Young Lady. This old servant is overwhelmed with gratitude for your great grace and kindness. How can such benevolence exist in this world! Ah, it must be a gift from the heavens."

"No, it's not all that………."

"No, it is. People tend to be greedy for other people's gold but stingy with their own coins. To give away such a fortune that could let you live in luxury for the rest of your life, this Geoltaran is moved, so very moved……"

"Well, it's not like I worked really hard to earn that money or anything. Don't make such a big deal out of it."

"Ahem. Your kindness will greatly help with the relief efforts, Young Lady. The funds were running low, you see. We requested additional funds from the main branch, but it takes ages to get there and back."

"Funds were running low?"

"Oh my, don't even get me started. The prices of food supplies are being jacked up like crazy. Grain prices are already nearly ten times the previous rates. For now, we're distributing what grain we have, one ration a day, but it's hard to buy more before additional funds arrive, so we were worried we'd just have to sit and twiddle our thumbs, you see."

Then he started praising her again-

"But at a time like this, Young Lady, you have descended with your noble presence and bestowed gold like a vast ocean of grace, truly-"

"Stop. Stop. Ah geez, even I'm getting embarrassed, listening to all that. Just cut it out. Anyway, I assume this would be enough, right? Will there be more expenses for the reconstruction work or things like that?"

"Ahem. To be honest, it's not enough for the construction, but at least we can feed the city for twenty days."

"Huh? It's not gold bars but coins, and over forty guan, yet it only lasts twenty days? I told you to provide relief, not throw a feast until their bellies burst."

"That's the thing, you see. Even with gold and silver, it's not easy to secure grain. It's ten times the price now, but if we show up with gold and silver, they'll ask for thirty or fifty times the price, and even then, they won't sell. They're bastards, through and through."

"What? Why? Are they insane?"

"That's just how merchants are, you see."

The floods were unfortunate, but for merchants, it was a golden opportunity to make a fortune.

Of course, those whose homes were swept away by the flood suffered, but even those who managed to preserve their homes didn't have anything to eat once the mud and floodwater receded.

That was when they would sell grain at wildly inflated prices and if people said they didn't have money, they would issue expensive promissory notes. So those who were starving would buy the grain, quickly ending up with all their property gone and nothing but debt left.

And all that debt would become the merchant's property.

"What? Why would they do something like tha………"

Qing frowned.

"Anyway, that means we need to secure the grain first to carry out proper relief, right?"

"It's ten times the price now, but if we show up with gold, they'll ask for twenty or thirty times the price. They're not the kind of people who would sell when you offer them gold and silver when just a few handfuls of grain will later turn into fields, livestock, and slaves."

At this, Qing shook her head.

"They're not conveying their sincerity properly. If you sincerely ask them to sell, how could they possibly refuse?"

"Oh, Young Lady. It would be nice if the world worked like that, but……"

"Well. Let's go. Since we're talking about it, we should go buy some."

Geoltaran was just fretting, worrying that Qing might be disappointed when she realized the harshness of the world because she was still pure.

However, this was a case of underestimating Qing's sincerity.

After all, Qing was someone who was always sincere when it came to screwing over bastards she didn't like.

Thus, Qing headed straight for the entrance of the Taecheong Merchant Association.

By then, the news of the relief efforts had spread, and people had gathered like clouds.

Thereupon, Qing climbed onto the table used for distributing relief rations and took her place.

"Everyone, unfortunately, we are running low on grain."

At this, the expressions of the people in line darkened.

Those at the back of the line had faces close to despair.

They were out of grain? When they didn't even have anything to eat. Other merchant associations were asking for a handful of silver for just a handful of grain……

As murmurs spread among the crowd, Qing raised her fist towards the sky.

Clang…….

The clear sound of Buddha's Palm silenced the commotion in an instant.

Qing smiled the most beautiful smile of the greatest beauty in the world and continued.

"However, I intend to fill our stock with grain by spending my personal fortune so that we can distribute it to everyone."

At this, the people's faces brightened again.

She was really someone who knew how to play with people, lifting their feelings up and down.

As everyone stared at Qing's beautiful face as if possessed, she continued to speak.

"But, you see. It's hard to secure grain even with gold and silver, so if we all gather our hearts and ask them to sell us grain, wouldn't they be moved by our sincerity and open their warehouses? Shall we all go together and ask them?"