\chapter{Drifting Off Course (7)}

To protect a mere merchant's guild, the city's magistrate had personally come forward.

A magistrate was the highest authority in a small city and the second-in-command in a province-level city like Nangnyeong, just below the governor.

Therefore, this was a very embarrassing situation. If other city magistrates heard about it, they would surely click their tongues and spit, saying, "Gold is gold, but you should consider your face as a magistrate. How could you make a personal appearance?"

The value of the magistrate's personal visit would, of course, be billed to the Jangheung Merchant Guild later.

However, what was more interesting was the fact that within just a couple of hours of Qing's purchasing grain from the merchants, the magistrate had appeared leading the constables.

It was an indication of the Jangheung Merchant Guild's influence.

Of course, for the usually slow-moving government to act so miraculously quickly, one reason alone was not enough for motivation.

Therefore, there were several reasons for the government's rapid response.

First, the leader of the Jangheung Merchant Guild was indeed sworn brothers with the governor of Shanxi Province, the highest authority in the province.

However, the governor of Shanxi Province was the governor of Shanxi Province, and this was the land of Henan.

Although he was a superior, it could be said that their networks belonged to different factions.

Saving the Jangheung Merchant Guild could put the governor of Shanxi Province in their debt and bring benefits later, but that alone was not enough to send the second-in-command in person.

Therefore, in order to balance the scales of the government's mobilization, an enormous amount of gold and silver, the magistrate's travel expenses, had to be placed on the other side.

But the biggest reason was that Qing had arbitrarily started the relief project.

Originally, for such relief efforts, it was customary to first notify the government and share the credit.

And if one were to say that a hundred gold coins were used for relief, thirty of them should first be given as a reward to the officials who had worked hard for the country.

This was the unspoken etiquette and procedure not prescribed by national law.

Therefore, upon hearing the news of the relief effort, the highest authority of Nangnyeong Prefecture, the governor, threw a fit of rage and immediately ordered them to bring that impudent and brazen wench to him.

In the correct order of things, Qing should have first appeared at the government office, paid her respects, and after giving ten of the forty gold coins to her superiors as a token of gratitude for their benevolent rule, she should have started the relief effort under the combined names of the government and Qing (with the government taking the lead).

If Qing had heard this, it was clear that she would not have held back, saying something like, "Heavenly Slaughter Star wouldn't endure this. I would have endured it, but not the Heavenly Slaughter Star. Did you really think I wouldn't lose my temper? Next year, today will be a joint memorial service for all the officials of Nangnyeong."

Isn't it just sitting there, eating gold and silver, and then putting your name alongside to pretend you did a good deed, and even making it seem like you led the effort?

However, the governor also had his justifications.

How much gold and silver did it take for an official to rise to the position of governor?

From the lowest ranks, he had taken bribes and illicitly accumulated wealth, exhausting his family's fortune and offering it everywhere to climb to the position he now held.

So, at the very least, shouldn't he recoup his investment?

Although the magistrate's face was disgraced by appearing in person, he was grinning from ear to ear, thinking of the hefty sum he would later extort from the Jangheung Merchant Guild.

This was the state of affairs in Zhongyuan.

Surprisingly, this was a common occurrence in all cultures derived from different cradles of human civilization throughout history.

Since it was a universal human culture regardless of East or West, past, present, or future, it could perhaps be said to be an inherent part of human nature.

However, Qing did not know this.

Nor did she want to know.

I'm just trying to help flood victims with my own money (not mine), so why are these government bastards interfering when they can't even help?

"Are you not going to move aside?"

"Do you not realize that you are violating the law right now!?"

"Huh? Me?"

"Did you not gather these people with your deceitful words?! Come, your intentions are impure. Is it not your aim to gather people like a band of thieves to raid the merchant guild and plunder their goods?!"

"Gather? Who's gathering?"

"Are you going to pretend you don't know? Behind you-"

"Wow, shit. That scared me. Hello, everyone?"

Qing turned around and pretended to be surprised.

At that, the crowd blinked, unsure of how to respond.

"Magistrate, sir. You're blocking the road, so everyone is standing here inconvenienced. Everyone, isn't that right?"

Only then did some people in the crowd begin to understand Qing's intentions.

"That's right!"

"Magistrate, sir, we were just passing by and were waiting because the road was blocked."

"Aigo, there are so many people, I can't even get through. I can't go forward or backward, what should I do?"

We didn't gather with any intention.

We're just passersby.

But the government blocked the road, you see?

So we had no choice but to stand here.

Qing looked at the magistrate as if to say, 'What do you think now?'.

"What, what kind of nonsensical sophistry is this……."

The shamelessness was so great that his brain had trouble processing it. It was almost as if his face was made of Cold Iron. No, was it Adamantium? Vibranium? Or perhaps his skin had reached a level akin to the legendary Diamond Is Unbreakable?

As the magistrate stammered, unable to speak, Qing smiled sweetly and asked again.

"Magistrate, sir. Are you not going to move aside?"

"Fine. Then, all of you, go back."

"Ah. Well, there's nothing we can do then. Everyone, the Magistrate says to go back, so we have no choice but to go back, it seems."

At the same time, Qing's hand moved gently.

Simultaneously, there was a clear and resonant sound of a Buddhist temple bell, going Deeeeng-!

At the same time, to Qing's left, the wall crumbled with a loud crash, as if it had been crushed!

It seemed the wall was too weak to withstand one of the Divine Arts Under Heaven, the Buddha's Palm.

Qing did not stop there.

Thump, she stomped on the ground, unleashing the technique of the Celestial Demon's Dominating Stride without any regard for appearances.

Heaven-Shattering Demonic Qi shot out from under Qing's foot, piercing the earth and causing an explosion under the already collapsed wall. With a low rumble, the very foundation shook.

The already collapsed wall, along with the ground beneath it, undulated in concentric circles, causing the wall to collapse to the left and right with a loud crash.

Thus, a wide passage was opened, easily allowing a large carriage to pass through.

"Now then. Magistrate, sir. You must be very busy, working hard to protect a mere merchant guild. Since you told us to go back, we have no choice but to turn around and enter that way. This girl will now turn around and enter."

"No! Going back is not what I meant b-"

"Hmm. What? Is some bug making noise?"

"You wench! What did you just say!"

At that, Qing grinned.

It was a smile so wicked and ominous that it was hard to imagine it coming from a beautiful woman.

"Magistrate, sir. Isn't a mayfly a truly courageous creature? They are so insignificant that they can easily be killed with just a wave of a human hand, yet when the air warms up in the evening, they block the road and fly around in groups."

By now, the magistrate understood what she meant.

And wasn't it clear to the naked eye that with a wave of her hand, a wall a jang1 high had collapsed, and with a stomp of her foot, it had crumbled once more?

A Master!

And not just any Master.

-Hmm. I should just kill him.

A soft murmur reached the magistrate's ears very clearly.

This was a technique called Sound Transmission. To be precise, it was similar to Sound Transmission.

Since Qing hadn't properly learned Sound Transmission, she was just clumsily imitating it.

The magistrate's heart dropped to his feet.

How could a whisper be heard from this distance? Was he reading lips out of a sense of crisis?

Meanwhile, Qing reached out to the magistrate.

The magistrate was greatly startled and immediately threw himself to the ground, rolling away.

Since it was the morning after a heavy rain and it was still drizzling, the ground was full of puddles and mud.

As the magistrate rolled on the muddy ground, a cute little bell sound, Doong, passed by his ears as if to tease him.

"Oh my, Magistrate, sir, why did you suddenly fall like that? You fell so intensely, too?"

"Y-You, you wench!"

"Ah. Magistrate, sir. I feel like I've made a mistake today, so could you perhaps tell me where you live? This girl will secretly, alone, and quietly visit you later to apologize."

The magistrate's mind went blank.

Secretly. Alone. Quietly.

If she came at him with a knife in the middle of the night, a magistrate or any official position wouldn't protect his life.

Then, five characters clearly floated in the magistrate's mind. Authorities cannot intervene in the affairs of Wulin!

Originally, Authorities cannot intervene in the affairs of Wulin was a phrase used by officials to protect themselves from the murderers who wielded swords and flew around.

This was because martial artists feared not the government, but the Imperial Palace, and the tens of thousands of cannons possessed by the Imperial Palace.

The Imperial Palace was the government, but the government was not the Imperial Palace, so if a martial artist decided to kill, they often couldn't even find the culprit.

In fact, martial artists often beat up officials when they felt like it.

However, the martial artists who were beaten by officials were usually vagrant wanderers who just imitated martial arts or were from small, rural martial arts schools.

Even the Celestial Emperor had his neck grabbed and was dangled from the top of the Imperial Palace by a peerless Master in the past.

Aigo, I've provoked a true Master.

What glory was there to gain by provoking a Master?

The magistrate reflected with intense regret.

Of course, it wasn't just regret.

"No! No! It is not that! The road was a bit slippery, so, ah, the road conditions are terrible! Isn't the drainage inadequate! Ahem."

For reference, drainage in Zhongyuan was something that had no solution in the face of a long rain.

It was an excuse that was that desperate and poor.

"Then, may this girl go in now?"

"Of course. Please, hurry and go inside, I mean, turn around."

What else can I do but go in since he tells me to?

Thus, Qing headed to the Jangheung Merchant Guild's manor, passing through the collapsed wall with light steps.

Behind her, the crowd also followed with a Woosh.

"Isn't this fine, even like this?"

"Aigo, my friend. Didn't the Magistrate say it was okay?"

Some expressed concern, but after the magistrate and the constables had been pushed back, the crowd's morale was sky-high.

And so, the Jangheung Merchant Guild.

Perhaps they did not expect to be broken through by a hole in the wall instead of the main gate, the guild's servants came out and blocked the way, pleading that they shouldn't do this.

Of course, there were far more people in the crowd following behind Qing, so they could only step back while pleading.

As they pushed forward like that, they wondered.

Just how big is this manor, anyway?

Then, a group of martial artists appeared next.

However, wasn't Qing someone who had already defeated many such groups while circling the merchant guilds?

Moreover, this time, Qing didn't even need to use her tongue.

"Young Lady Ximen, it has been a while. Do you remember me? I am So Juhang, the first disciple of the Nangnyeong Martial School. We met at the Yongbong Assembly."

Who the fuck is this guy, trying to act all friendly?

But Qing was now a proper martial artist of the Orthodox Faction, so she wasn't so tactless as to ask, 'Who are you?' to someone acting friendly like this.

"Ah! Young So! It has been a while! I was disappointed that I could not greet you when you left, but it is truly a pleasure to see you again like this!"

Though she had no idea who he was.

Qing pretended to be very pleased.

This was the courtesy of the Orthodox Faction, which valued saving face.

So Juhang understood this too, so he had a slightly awkward expression.

But thanks to this, the claim that he had been boasting about, saying he knew the Heavenly Flower, was now a fact.

It was a moment when he felt endlessly grateful for Qing's consideration.

"I was planning to visit the Nangnyeong Martial School first and greet the Sect Leader, but I forgot in my haste due to the great disaster that has befallen the city. Is the Sect Leader well?"

"Ah. Of course."

"I would like to have a conversation to catch up, but I am on my way to ask the branch manager of the Jangheung Merchant Guild for help with the relief effort. Would it be alright if I passed by?"

"Of course, of course!"

Thus, the Nangnyeong Martial School was defeated!

Passing by the martial artists of the Nangnyeong Martial School and continuing to walk towards the largest building, another person appeared to block the way.

He was an old man with a dignified presence.

He was already raising his Inner Qi, creating an extraordinary aura, so his presence was far from ordinary.

Qing's expression automatically soured.

What, a Transcendent Realm? No, Unrestrained Realm?

No, why do Masters keep popping up everywhere I go?
