\chapter{Drifting Off Course (3)}

The crowd split apart at the tip of Qing's outstretched sword.

It was as if a cannonball had been fired from the tip of her sword, causing a commotion as people parted to the left and right, creating a gaping hole in the once-impenetrable encirclement.

It was a well-opened, straight, narrow path that showed the open space beyond.

And in the middle of it, as if there was a disturbance, a man was pushed out onto the path.

The man stumbled and, upon seeing the tip of Qing's sword aimed at him, turned pale and tried to scramble back into the crowd.

What's this? Does he think some kind of beam is going to shoot out of my sword or something? But, hmm. This is a bit interesting.

However, the man was roughly pushed back by the crowd, falling and hitting his buttocks hard on the ground.

"I-It's not me!"

"Don't be ridiculous! You were the one who shouted!"

"I heard it clearly from right beside you!"

Qing's eyes narrowed.

"What's going on? You were so bold when you were shouting, but now that you're out here, you're backing down?"

"Th-That's."

"What do you do to keep making such interruptions? Hmm. Do you perhaps know this person?"

Qing asked the designer.

But the designer just shook his head.

"I do not know him."

"He says he doesn't know you. Does anyone here know this person?"

Qing was someone who knew how to ask when she didn't know.

And indeed, the power of collective intelligence was great.

"Isn't that the server from Jeha Restaurant?"

"That's right! Now that I think about it, I've heard that voice before!"

Unlike Qing's hometown, in Zhongyuan, the affection between neighbors was still alive and well.

And the affection between neighbors was also information, so if you lived in any neighborhood for just a week, you'd come to recognize everyone in the whole village.

Thus, his identity was quickly revealed due to the enthusiastic responses.

"A server? No wonder his voice was so loud. Hey, why do you keep interrupting?"

"That's, I clearly heard it back then!"

Seeing his opportunity, the server poured out his story.

Last winter, when the construction was in full swing, the carpenters from the Jangheung Corporation had come for a company dinner.

Originally, dinners involved alcohol, and when the alcohol content exceeded a certain level, people would blurt out things they should and shouldn't say.

And, strangely enough, whether in Zhongyuan, the West, or Qing's hometown, people tended to treat servers as if they were part of the background, not as human beings.

Thus, the server had clearly heard.

"They said it was a ridiculous design from the start! Who in the world would build a riverbank like that and stack a levee like this? They cursed, saying it was a design made by someone who had never even experienced a construction site, someone who only knew theory!?"

"Oing."

Qing looked at the designer again.

The designer's expression distorted.

"Where is it a ridiculous design!? From the foundation to the structure, it was designed to be as easy as possible, just build and fill and stack! Isn't that why the government chose my design!?"

Qing didn't know anything about civil engineering terms, and even if she did, the terms differed between Qing's hometown and Zhongyuan, so she wouldn't have understood anyway.

The server stammered at the designer's protest.

"W-Well, I don't know about that…… I just heard it like that……"

"This is really an outrageous person. In a situation where people are dying, isn't shouting like that just like praying for their deaths?"

"But this mess is because of that guy."

"Whether it's because of this person or not is yet to be known, isn't it? If it's revealed later, then we can hang him or burn him."

"Well……"

The server avoided eye contact.

In fact, in the face of a great disaster, it was a natural human instinct to look for someone to blame.

The history of humanity was the same as the history of scapegoating. It was a defense mechanism to soothe the burning insides by somehow resolving the unbearable feeling of having nowhere to vent.

"But Jangheung Corporation?"

"It's the corporation in charge of the flood control project."

The process of the flood control project was as follows.

When the government announced a flood control project, consortiums would apply and a construction company would be selected.

At the same time, they also solicited designs and selected an outstanding one among them.

After that, the government would provide the selected consortium with the design and construction funds.

As an aside… The reason for collecting designs and construction separately was to have an anti-corruption measure in Zhongyuan.

However, the officials of China had never been uncorrupted, from the past to the future.

Originally, the design should have been created and provided by the government's water management official.

However, the position of the water management official was effectively a non-existent position, used to embezzle funds by placing the name of a superior's son, friend, or even a fabricated name on the official roster and siphoning off the salary.

Therefore, under the pretext of giving opportunities to talented individuals in the private sector, they solicited designs.

It was a chance to 'bestow' an opportunity to make a name for themselves, so of course, no design fees were given.

Rather than payment, it was an honor for an official to select a design without accepting bribes.

"Jangheung Corporation. So if the design was fine, it means there was a problem with the construction."

"Ahem."

"The Jangheung Corporation is a bit."

"Mmm……."

Somehow, the reactions of the crowd were lukewarm.

What's this? Why?

I thought they'd be shouting to burn them at the stake or something.

As the name of the Jangheung Corporation came out, the atmosphere sank, and everyone sighed, slumped their shoulders, and gradually dispersed, disappearing.

What's with this atmosphere?

It's as if there's some taboo, like a name that can't be spoken, like a certain someone who must not be named.

While Qing was bewildered, wondering what was going on, the designer bowed deeply.

"I haven't properly thanked my benefactor. My name is Yak Joongyoon, and, child, you should also greet your benefactor."

"I'm Yak Jijun."

"Hmm. So what are you going to do now? I think it would be dangerous for you to stay in the city."

"That is true, but the roads are a mess and the times are uncertain, so it's not like we can just go anywhere."

After a disaster, robbers and thieves were rampant.

Although the city was dangerous, it would likely be safer than the current roads.

"Hmm. I'm on my way to the Naknyeong Martial Hall, um. Perhaps I could ask if they could offer you some protection for a while."

"How could I be such a burden? Thank you, thank you. I never knew words of gratitude could feel so insufficient."

"Hmm."

Qing made an awkward expression.

It was called protection, but it was also surveillance.

After all, there was no guarantee that the design was completely sound and without problems.

If the person was innocent, it would be protection, but if it turned out later that the design was the problem, then it would become confinement.

As they were vaguely dismissing the crowd, Yak Joongyoon offered to drive the carriage, so Qing, leaving behind the horse's rump that she had started to get attached to, got on the carriage.

She tried to.

"Young Lady! Young Lady Ximen! I see you here!"

"Oing? That."

Qing tilted her head.

Someone was being very friendly and making a fuss, but, um, who are you?

His face seemed familiar, so it wasn't completely unfamiliar, but if asked who he was, she had absolutely no idea.

"Who are you? Do I know you?"

Qing scrutinized the man.

With thick calluses on his hands and numerous scars, he seemed like an average martial artist, but…

It's strange.

I've never shared a meal with a martial artist other than Shaolin monks, have I?

Ah. There were those ronin, huh. But he doesn't look like a ronin?

At this, the man made a fuss.

"This lowly one is called Geol Taran. We have met a few times at the Seolga Corporation, so of course, you wouldn't know me, but I was so moved and thrilled to see you that I ended up making a scene. Hehe."

"Ah. Are you from a corporation? What brings you here? What, did the Seolga Corporation expand this far?"

"Please, lower your speech. And I am the branch manager of the Taecheong Corporation in Naknyeong."

"Eh? You changed jobs?"

"It's an alliance, a brotherly corporation. Mm. That's right. If I had to say."

Geol Taran made a circle with his thumb and index finger and continued.

"Let's just say the owner is the same."

"Ah. The owner."

Qing immediately understood.

Whether it was the Seolga Corporation or the Taecheong Corporation, it meant that the person who provided the funds and held the majority stake, or the parent company, was the same.

What Qing didn't know was the identity of the owner.

The owner was the Heavenly Demon Divine Cult.

Thus, a Special Agent of the Demonic Cult's Espionage Unit (formerly a Special Assassin, the job title had changed) was overwhelmed with emotion upon seeing Qing.

Moreover, when Qing had instantly subdued the crowd with her footwork, the immense majesty he felt from that had him holding back tears of admiration by a hundredfold.

He was also holding back the urge to prostrate himself by five hundredfold.

"Hehe, please lower your speech."

"No, how can I do that? I'm not someone affiliated with the corporation or anything."

"That's not it. Lord Choi specifically told me to treat you as an elder. This time, he started a new corporation with investment from the owner. So you are also an elder to me."

"Hmm. Is that so?"

Hmm. Gramps. He sure is capable.

Gramps' corporation, huh.

Qing asked just in case.

"By any chance, the name Taecheong Corporation……"

"Hehe. Of course, it was taken from your name."

"No, why are you using someone else's name as you please?"

Seriously, how burdensome.

But if it's Gramps' corporation, maybe I can make use of them?

"It's a good thing we met. The city is in this state, so I was thinking of offering some relief……"

"Oh my, how could you be so compassionate? As beautiful as you are, your heart is just as kind."

"Hmm. I have some gold, about forty ingots. How much help would that be?"

"Please, lower your speech……"

"Uh, okay."

It was a bit awkward for Qing to lower her speech to a complete stranger.

But Geol Taran seemed satisfied.

"Gold, you say? But we are already preparing relief, so you don't have to share your precious assets."

"Oing. You're already preparing relief?"

"Please, make yourself comfortable with your words……"

"You're already preparing relief?"

"Yes. What use is business when a city has been struck by disaster? We must first help people live."

That was the case, but the original purpose of the Taecheong Corporation was to provide relief in the first place.

It was a dirty trick by the Heavenly Demon Divine Cult to infiltrate Zhongyuan by winning over the hearts of the people through such relief!

It just so happened that they had subtly infiltrated the land of Hanam just in time for the flood season, and a flood had actually occurred.

As a result, Geol Taran had been singing praises all night long after seeing the city swept away.

He thought that the heavens were looking out for the Divine Cult, giving them such a golden opportunity.

"Hmm. You're doing good things. No, you are."

Qing, not knowing the situation, said so.

But even if she knew, she would have said the same thing.

It wasn't like they intentionally caused the flood, so if the goal was a bit impure, wasn't relief still relief?

"Hehe. Could you praise me a little more?"

"Uh. Good job? Excellent?"

"Keuheuk."

Suddenly, Geol Taran's eyes turned red.

After all, wasn't he receiving praise while facing none other than the Heavenly Demon Supreme?

And not just any praise, but praise for his work.

O, Heavenly Demon Supreme.

My light, my salvation, the reason for my life.

Qing, unaware of the situation, just felt a bit put off.

Hmm. Is it that big of a deal to be this moved over?

Is he a bit strange?

Is Taecheong Corporation okay like this?

Using someone else's name to do bad things is a bit…

"Still, good things are better when there's more. I was worried since I just entrusted the gold, wondering if it might leak, but this is a relief."

She had been thinking about how she had nothing but gold ingots and wasn't sure how to go about providing relief.

She had been thinking of entrusting it to an Orthodox Faction martial hall and using her name, thinking they might use it diligently. That was why she was heading to the Naknyeong Martial Hall.

But if it was Gramps' corporation, she could trust them and just hand it over. 