\chapter{I don't believe in legends (6)}

Qing was waiting for the food and drinks.

Once you place your order, it takes forever for the food to arrive.

It's too long…

Everyone had a hard time eating, sleeping, and cutting meat in the mountains, and then came down and shook their bodies.

Everyone was just leaning back in their chairs, their eyes blank and drooping.

Chen Changming even nodded off.

It was during that time.

One guy was approaching the table.

When Qing looked up, she saw a handsome beard visible under his hat.

It doesn't look like it's been particularly well-maintained.

That kind of appearance was something you just have to be born with.

But? Who was it?

Among the people I know, there was no one with such a nice beard.

There was no one there who uses dual swords.

"Excuse me. From what I've heard, it seems like a lot to eat. Can I help you with a little bit?"

What the heck, this kid.

Qing was speechless.

All you can say after coming here was ask for some food.

And that too in a very shameless way.

Except for Chen Changming, who was sleeping, the teacher and Murong Zhu Xi also looked at Qing with expressions of bewilderment.

Do you know him by any chance? What are you going to do?

Qing's gaze glances upwards.

Wouldn't it be nice to see a blue number that'sn't used in Zhongyuan?

What? He's a good guy?

Qing was very generous to the sages.

And it doesn't seem like the three of us will be able to eat properly.

"I can't help it. It's just this once."

"Huh? Really?"

Then the man was surprised.

I guess he didn't think I would give permission so easily.

"Why? You said we should eat together?"

"This isn't fun."

Qing's eyebrows straighten out.

What fun?

If I say no, do you want the fun of taking it away?

How hungry must you be to come to someone else's table and ask for food? I felt sorry for you and allowed you to eat with me, but now you're sitting there having fun?

Should I just kick him out?

It was when Qing was thinking like that.

"Hey, swordsman. Let's go."

The man lifts his hat slightly.

Qing's eyes widen.

A familiar face appears there.

This was Nan-gong Shencai with a beard.

"No. What was it? What are we doing here?"

Chen Changming wakes up with a start at the sound of Qing's welcoming voice.

"He ran away from home."

"Hmm."

Come to think of it, wasn't he running away from home when we first met?

I thought, "He's just a friend who likes to run away."

Meanwhile, Nan-gong Shencai bows his head.

"Excuse me, sir. I am Nam Jae, this friend's swordsman friend. I did this to tease my friend, so please be considerate."

"Well, that could be the case."

"How are you, young lady?"

"No, you."

"Call me Namjae, not you."

Of course, Murong-ju also recognizes Nan-gong Shin-jae.

Nan-gong Shencai sits down on the chair with a cheerful smile.

"Yeah, guys. Uh, I can't remember what their names are."

When you say you don't remember the name, you're saying you're in disguise, so what should I call you now?

"Here was Baekjang for the elder, Baekil for me, Baek-i here, Baek-sam over there."

I changed my name because the Gangpaecheon guys would come looking for me.

Anyone who hears it knows it's a fake name, but since fake names are everywhere in the city anyway, no one will really care.

"That's right. That's right."

And only then did Qing become curious.

Asking what you're called means that you've recognized my disguised state.

How? I can't tell even when I look in the mirror.

"What, what, how?"

"That's right. Arm length and leg length are the factors that determine a swordsman's skill, based on his range of swordsmanship and stride length."

This was an answer that says that you can tell by looking at the height, arm length, and leg length.

"……?"

Qing tilted his head.

No, do you usually recognize people by that?

Is that possible?

Qing casts his gaze at Tian Yuxue.

Can you really tell people apart from that?

Tian Yuxue shakes his head and responds.

How could that be?

"Let's eat first."

Qing and his party came down to the first floor, leaving the private room behind.

why?

Because Qing has no thoughts?

Of course, it's a very valid inference.

But unfortunately, this was Tian Yuxue's opinion.

It's very suspicious that he entered the highest-class guesthouse in such a beggarly state.

If you use a separate room at a time like this, there will be people who will find it even more suspicious.

And the suspicious guys live in the border.

In that case, it would be better to just show off the exquisite art of eating magu on the first floor and attract attention.

Because once they become a spectacle, they no longer seem suspicious, they just turn into strange guys.

They say that suspicious people don't do anything that stands out.

So that's what Qing did.

A plate of food that keeps getting emptier, and three meals!

The guests glanced at first, then stared openly, and then watched the inhuman eating scene as if entranced.

Indeed, will I be able to eat all of that?

A breathtaking sight that will have you on the edge of your seat.

And finally, Qing puts the last piece into his mouth and raises his fist.

Then, applause, whistles, and cheers fill the room.

-Whew! "You're eating well!" "You're a true food spirit! You're a food spirit!" "A food spirit? Haven't you ever seen someone eat? You're not a food spirit, you're a mountain lion!" "Amazing!"

"Sanjeo!" "Sanjeo!" "Sanjeo!"

"Jeomsoi! What was that food you just ate over there!?"

It refers to a wild boar.

Qing's eyebrows twitched.

Sanjeo? What kind of kid started it?

Anyway, thanks to that, the guest house became bustling as if a feast was being held.

As if the sight of Qing's delicious food whetted her appetite, Jeomsoi runs around busily to the sound of people ordering food here and there.

Meanwhile, the Qing party went up to the room.

"This was my second teacher. Teacher, this was Nan-gong Shencai. He was the grand duke of the Nan-gong family, correct?"

"That's right. Hello. I couldn't properly greet you earlier because I thought you were using a false name. I'm Nan-gong Shencai. I'm a close friend of yours, Lady Ximen."

In fact, Tian Yuxue had already seen Nan-gong Shin-jae several times.

It was when I was pretending to be a worker for the Wulin Alliance.

Of course, even if Nan-gong Shencai had a peculiar eye for detail, he would not have memorized the length of the arms and legs of a certain member of the Wulin Alliance, so it would only be their first meeting.

So, Tian Yuxue knows the expression "geomwoo" because he has heard it several times.

But this was the first time I've heard of Chen Changming.

Chen Changming pokes Qing's side.

Since Qing was ticklish, she fell asleep right away, as was natural.

"Gyaaah, what the heck, I'll just ask."

"Yeah. What was Geomwoo?"

"Little Brother! Did you ask what a sword is? If so, it's only natural that I should answer!"

Qing tilted her head.

Can we prevent the destruction of the world and keep peace?

Did the swordsman have such an obligation?

"Sword Friendship was an expression used only by true swordsmen, referring to a friendship forged through the sword. No, the word "friendship" was too trivial to describe the close bond between sword friends. Do you understand what I mean?"

"I don't know."

Of course, I couldn't know.

"But where was Confucius here?"

"Ah. This was my younger brother, Chen Changming. He was a disciple of the Shinnyeomun. This was Nan-gong Shencai. He was the grand duke of Nan-gong Segae."

"Ah. Oh dear. I've made a mistake. The young lady has been so rude that she's accused me of something."

The tendons on Chen Changming's forehead bulged.

Not all women are happy to be told that they look young.

This was a taboo that should not be said to women in their twenties.

Plus, it's a bit weird to hear people say you're handsome right in front of you.

Nan-gong Shencai was not called Geomchi for nothing.

He was the owner of that amazing wit that allows him to talk about half-swords while staying in the Taoist temple.

So, just because you are in front of a woman, you don't start to notice things you didn't know before.

To be exact, it's not that he's oblivious, but rather that he just doesn't notice things.

"By the way, what are these twin swords?"

I have carried several swords, but I did not carry them left and right, but rather carried them side by side to the left, or if I felt like they were going to fall, I carried them behind my back.

Because you have to pull it out with your right hand.

But Nan-gong Shencai had one on each side.

Doesn't that mean you're going to use dual swords?

"Oh, my. Geumwoo. I'm so disappointed. Can't you recognize me? This isn't some kind of twin sword."

The tendons on Murong Juhee's forehead also flared.

Of course, the twin swords are a symbol of certain defeat.

But that's not something you should say in front of someone who uses those twin swords.

But Nan-gong Shencai was a true swordsman.

Even if it's a little better than those who use other weapons, there's no need to worry about the feelings of someone like a dual swordsman.

"This was it. It's a double-edged sword."

"Huh."

"Don't you understand? Dual swordsmanship presupposes the use of two swords. To claim two swords as one martial art? Then isn't it no different from half-swords?"

Murong-ju-hee lights a twin flame at him.

"What did you say? And the dual swordsmanship of the main family isn't about one swordsmanship, but about harmonizing two swordsmanships."

"Pride was good, but don't you know, Lady Murong? Each swordsmanship doesn't exist in isolation. Wasn't this martial art originally created with dual-wielding weapons in mind? As far as I know, the paths the left and right weapons take are skewed left and right, up and down?"

"That's to prevent the sword path from getting entangled-"

Nan-gong Shencai cuts off Murong Juhee's horse.

"Isn't that just an excuse, after all? But for a true swordsman, the different swordsmanship styles should operate independently. Shouldn't the sword complement one another? Shouldn't two distinct styles be deployed in the hands of a single swordsman?"

"That's impossible. If you use two swordsmanship techniques other than dual swordsmanship, the sword paths will inevitably become entangled-"

Cut off the horse's tail again.

"Who said it was impossible? Isn't martial arts always about overcoming and transcending the impossible? If I swing it ten thousand times and it doesn't work, I'll swing it ten thousand more, and if that still doesn't work, I'll swing it ten thousand more. I've decided to see the end of my sword, so I will strive endlessly and overcome it."

Those were truly wonderful words.

But Murong-ju-hee, who was interrupted not once but twice, was seething with anger.

It's even more annoying because the way he answers seems plausible.

Isn't this the story of Ugong and the mountain?

Once upon a time, there lived an ignorant old man (Woo-gong). He came up with the ignorant idea that in order to develop his village, he had to clear the mountain.

Every day, he would dig up dirt from the mountain and throw it away far away. A smart old man (Jisoo) couldn't stand to see that happen and tried to stop him.

Then the ignorant old man said:

If I don't do it before I die, my children, my grandchildren, and my grandchildren's grandchildren will dig the ground, and then one day that mountain will disappear.

It was a level of tenacity that makes you believe that your shoulders will become stronger the more you use them.

Isn't this even the equivalent of forcing children and their descendants to do this stupid thing for generations to come?

That's why it's scary when an ignorant person has faith.

So the mountain spirit also became afraid.

So I asked the Jade Emperor to stop that ignorant old man.

Oh my.

Even the Jade Emperor was a possessor of the theory of nature!

There was a story about how he was moved by the great spirit of the old man, who even sold his descendants, and moved the mountain.

Thus, the Taoist classic "Yugong and the Mountains" was a saying that praises Yugong's tenacity and mocks the clever elder who gives up in fear without even trying.

So, Murong-ju has no intention of playing the role of a smart old man.

I just thought it would be best not to talk to crazy people.

And in fact, it's the smartest way.

"But why was Geomwoo disguised? I was wondering if he was Geomwoo, so I watched him, and when I saw him ordering food, I was certain."

"Ah. That's…"

Qing confessed her story.

The appearance of the evil vampire!

The massacre of the Sapa was even more evil than that!

And so, like a lucky charm, a chain of resentments follows one after another!

This grudge-spinning began with the Blood Cult's attack, and spread its grudge around Mount Lao, and within a day, the Gui sect attacked another sect…
