\chapter{I don't believe in legends (4)}

If you ask what kind of people the Blood Cult is, you will get various answers.

Something wearing human skin.

Those damned evil creatures on the edge of humanity.

Those damned bastards who find joy in murder, plunder, rape, torture, and destruction. (Except for rape, someone comes to mind.)

However, not all blood cult members feel pleasure from killing people like Mr. Ximen or Mr. Qing.

Of course, the higher the rank, the stronger this tendency becomes.

But how could the members of the secret world-subversive group operating behind the scenes in Zhongyuan be all made up of such people?

Blood Cult was a group of people who feel sorry for themselves.

People who feel sorry for themselves.

Where can you find a grave without a story?

The stories of the Blood Cultists are each and every one of them incredibly strange.

They are people with such a sad past that they harbor so much evil and anger in the world that they want to burn it all down.

After hearing it, you may feel quite sorry for it.

But do you know what the easiest way for a person to get out of their comfort zone is?

It was about pitying yourself.

Because we have to look after the poor.

Even in the homeland of Qing, with its developed judicial system, weren't livelihood crimes not subject to reduced sentences?

Even if that's not the case, judges are people too.

When I see the poor, the rich, the powerful, and the retired former officers, I can't help but be generous.

Even the first judge who takes care of the poor was held up as if it were some kind of good story.

The whole neighborhood, this judge here, the absolute being in heaven, the judge of good and evil, the noble judge who was born different from the commoners, the noble judge, took pity on the commoners! Isn't that beautiful?

In this way, being generous to the poor was considered a virtue by humans.

In some ways, you could say it's a human habit.

Anyway.

The problem was that he was a pitiful person.

A person who feels sorry for himself was willing to look after himself.

I'm pitiful, so even if I cause some harm to the world, it's because there's a reason for it.

This Zhongyuan society has made me feel sorry for them, so they should let me kill and dismember some people.

Because I am a poor person.

Because he was such a pitiful victim who was harmed by the government, the martial arts people, Zhongyuan, and the heavens.

I am a victim.

It was a miraculous state of mind that allows you to hold your head up high and be proud, not to mention forgive yourself.

So wouldn't even that vicious thousand-year-old use it as a method to seduce humans?

And the Blood Cult was once again abandoned by the world and heaven.

Blood Lantern Double-Armed Combat Plan!

The Bloody Plan was an operation that causes the world to overflow with blood.

It's a childish name that only blood cultists would give it.

And the two-faced concept was that two-faced concept.

First, gather the Sapa by using the absorption magic as bait.

After that, he brings in the party a beat later.

The Jeongpa guys, worried that the evil magician might fall into the hands of the Sapa, would rush in in panic.

If the land was oversaturated with both the Jeongpa and Sapa unmanned forces, there will be a moment when they will collide and cause a huge explosion.

Of course, if someone plants a detonator along the way and connects the wick to light it, an even bigger explosion could occur.

This was the Blood Lantern Plan, the Double-Paced Plan.

But somehow the plan didn't fit together properly.

It all started with a failed extermination operation.

By displaying the pride of the Wulin Alliance, the Five Flowers of the Martial Arts Alliance, in a miserable manner, the influence of the Martial Arts Alliance was completely destroyed.

Then, it will be difficult to control the martial artists of the two factions at the stage of forming a two-party system, and their unity will also be weak.

Even the Jeongpa bastards are ultimately unmanned, so there will be more than a few who fall for the temptation of killing and killing that guarantees them the best in the world once they learn it.

The correctness of a political party comes from the senses.

The extermination operation was not just for fun or to save face for the Wulin Alliance.

This was the cornerstone for getting rid of the harsh glances that the Jeongpa Unin were sending each other, saying that they should be kind.

Even the Jeongpa guys are ultimately martial artists.

In the end, a martial artist was just a robber with a knife.

If only there was some chance, we could get rid of the disgusting pretense and hypocrisy of those political bastards.

however?

Rather, it only fostered unity, saying, "We defeated the Blood Cult!", so the successful martial arts competition was held to make people even more wary of each other, rather than just avoiding the spectacle.

I wish it had just failed.

The problem was that loneliness seems to have leaked out.

The livers planted in various places continue to be erased.

Because of this, it became difficult to convey news of the absorption magic to the Jeongpa.

The Sapa guys have gathered a lot of people, but the Jeongpa guys are all stagnant.

They sent a few groups or people nearby, but even then they didn't actively search for it, just stayed in the city and watched as it went away.

In the meantime, it's raining.

The passage was filled with water and poison was released.

The blood cultists wore gas masks that made it difficult to breathe, and they dug ditches by scooping out water and splitting rocks…

Oh my heavens!

Why was it that there was never a single time when you don't interrupt me!

That's how much we hate ourselves!

Why are you so cruel to us!

We poor bastards are truly abandoned children who should never even achieve our long-cherished dreams!

Aren't we pitiful!!

How pitiful we are!!

Why! Why can't we be happy! Why!!!

If the heavens heard this, they would be speechless.

Did I interrupt? Another girl interrupted.

The world's worst bastards' plot was stopped by the world's worst bastards.

This was the law of the world, where evil comes out and gets punished.

And here, another ordeal befell the poor Blood Cultists.

"Excuse me, Mr. Manbakja?"

"why?"

"Those, those Sapha guys, um. That's it."

"What? Can't you speak properly?"

"They are killing each other."

Half of the female dragon's face trembles.

In fact, if you want to drown the martial arts world in blood, you just need to reduce the number of factions.

Even if you leave those Sapa guys alone, they are the type of people who naturally call for blood.

But are those Sapa guys actually fighting among themselves?

While the political bastards are still thriving?

"What? Why? Weren't we doing a good job of searching the area by going around? Why are the already weak Sapha guys fighting instead of the Jeongpa? They may be stupid, but they weren't that foolishly stupid, were they?"

"Well, um. It seems like a cult of another bloodline has intervened…"

Kang Pae-cheon went on a rampage, vowing to find the evil spirits of the Blood Sect and take revenge on So Cheon-ju.

And as if by chance, large and small groups of people were attacked.

As luck would have it, the successors were killed right after the Sapa Martial Arts Competition.

So they started to call each other their enemies and started to stab each other in the neck, and now they are so busy fighting among themselves that they have put the treasure on the back burner.

"Well, thanks to that, the ronin and nameless rascals were able to fill the void."

"Those guys exist, but whether you get rid of them or not, it doesn't matter! But revenge on Socheonju? Gangpaecheon? What does that mean? Why was the name of our religion mentioned?"

"That, that name was Yun Yuanying……"

"No, that girl. Why…"

The dark dragon was so shocked that he just opened and closed his mouth.

I raise my hand and cover my eyes.

"Elder?"

"I didn't want to talk to that girl. She's kind of creepy. I wonder what she's thinking."

After muttering like that, Amharyong approaches a wooden box placed in a corner of the operation room.

It was a small box that could hold about a sack of rice, and it was locked with many locks.

As the dark dragon unlocked the locks one by one and finally opened the lid with a creak, surprisingly, a single person was barely able to fit in, his body curled up.

"Huh."

The subordinate held his breath at the sight.

Just looking at the body crammed into that small box was so gruesome that it makes you shiver.

However, the head that had been excessively bent suddenly straightens up, and with half of the face clearly showing the marks of having been crushed, the mouth opens wide.

"Ah, why are you waking up someone who's sleeping? They're old and have no manners. That's why you should kill them when they get old."

A beautiful woman with a wicked mouth.

And then, after wiggling her tightly packed body, she finally gets up and her voluptuous body was revealed.

It's not a volume that can fit in a box.

"Stop talking nonsense. Contact your master."

"Am I your mother's subordinate? It was comfortable when I was locked in a box, you know. Now you even have to give orders? Do you think I can live with this kind of sadness?"

"You b*tch-"

"Please. Please …

"You don't seem to know the situation, but your mistress was about to ruin the entire plan. If you want to save her life, why don't you bring her over right now?"

"Then there's nothing I can do. Sister, are you there? Yes, Master. Yes, yes. Hmm? Oh, okay."

And the shaman stares intently at the dark dragon.

The female dragon speaks in a growling tone.

"You, bitch, what the hell are you thinking?"

Then the shaman answers.

"I didn't connect. The master was sleeping right now. Is this urgent enough to wake him up?"

"The sun was high in the sky, how can you be sleeping? Can't you wake me up and connect right now!?"

"Anyway. With such a foul temper, his wife and children all ran away."

"What!?"

"Sister, it must be urgent. Yeah. Yeah. I can't help it. That's right. I'm so dirty, damn it. Yeah. Ahh. With the most beautiful voice in the world, haa, even the master's sleepy jade voice was beautiful. What's the matter? I was just enjoying a nice nap."

"What on earth are you thinking? Why did you come all this way to cause trouble?"

"What ingenious schemes are you employing? I feel this dull fool was oblivious and was hindering me. Please, offer your opinion."

The message was distorted to the point of being completely new, and Amharyong ground his teeth.

I used so much force that my teeth broke.

If we take out the intermediary's words and continue the conversation in different spaces, it would be like this.

"Why are you interfering? Don't you know how long we've been preparing this plan?"

"Oh my, what a nuisance! What kind of nuisance was that? That's what I have to say, having been interrupted from my sweet, sweet nap."

"Don't act like a fool! Your name was already being mentioned in the news right now! Why did you beat those Gang Pae-cheon bastards to death?"

-What are you talking about? I'm having a hard time hanging out with the Malgal people here.

The Malgal people are a strange thing to say.

Because in Zhongyuan, being called Malgal was a severe insult and a harsh term of abuse.

Even the Jurchen would deny their bloodline and tremble at the mention of Malgal.

That's why this year was so ugly.

At first glance, he seems polite and submissive.

But Amharyong's intuition tells him that this girl will never truly follow the Blood Cult.

And although the dark dragon's intuition didn't come often, when it did, it was very accurate.

"Don't act like a fool. Aren't you using those corpses to swindle people? Or who in the world would pretend to be a member of the Blood Cult?"

Since Qing was not from Zhongyuan, he can readily impersonate the Blood Cult.

It's like, what's the problem with that?

But the average person in Zhongyuan cannot even think of such a thing.

Impersonation itself was quite shameful, and impersonating a member of the Blood Cult was a terrible thing to even mention.

So, it's said that the Qing entourage was also shocked as if the sky was falling when they saw the Qing's atrocities.

Of course, Qing didn't really pay much attention to it, just wondering if it was something so shocking.

"Oh my, a living corpse? That's too harsh. And commanding them? Those who are like me aren't really members of the Blood Cult, are they? They simply listen to my requests. I don't force them to do anything. They're not my subordinates or subordinates. I don't have the power to control them, though."

"A shaman can't control the shaman I created? Are you expecting me to believe that?"

"Even if you don't believe me, it doesn't make it a lie, does it? Hmm. But I'm a little concerned. So, what do you want me to do? Should I go and catch the impersonator myself?"

"Well then! In any case, shouldn't you be the one to clean up what happened in your name?"

Actually, it's forced.

What crime did the person who was impersonated commit that he or she would have to deal with it or not?

Rather, it's a blatant evasion of responsibility.

'Anyway, it's your fault, so you have to fix it.'

Whether it's through direct contact or through the use of a shaman, if Yun Yuanying interferes with the plan, she becomes a party member from that point on.

Then, all the blame for the Daegye's mistakes can be placed on Yun Yuanying.

It's a sly old man's excuse to get away with it.

Yun Yuanying, unaware of such speed, answers calmly.

-If that's what you want, how could I refuse? Do you really want me to deal with the imposter?

"okay!"

Unyeonyoung answers him.

-Then, I have no choice but to follow your will.
