\chapter{I don't believe in legends (1)}

The Gangpaecheon warriors were greatly shocked.

It was such a huge shock.

Because the little lord died.

In fact, even if Elder Il died, everyone would have pretended to be sad.

If that old monster, who ruled like the real power in the sect with the young master, disappears, the other elders will nod their heads and say, "He died well."

The deaths of the Ilgye-wi and Ilgye-wi brothers are not particularly sad.

Aren't they the bastards who ignore the hierarchy and support the young master, and aren't they future competitors?

But the young master must not die.

Having lost his successor, he was worried that the anger might be directed at him.

In the end, I only worry about my own well-being.

I wish the young master had died kindly.

To the survivors of the village, the young master was the greatest enemy of all, so they did not even leave behind a complete corpse.

They smashed his head with a stone, separated his bones and flesh, and ripped out his internal organs and scattered them.

The only parts that are intact are part of the neck and the lower part attached to it.

So, the Gangpaecheon warriors also counted the number of corpses and looked at each other with trembling eyes, wondering if these were the remains of the young master, the Socheonju.

My fervent wish was that the Blood Cult bastards kidnapped me and brought me another body, please, please.

So, I was so distraught and confused that I didn't have time to pay attention to the fact that not a single sword was left and everything was gone.

It's not so unnatural for a villain to carefully collect weapons that have lost their owner.

However, it's not only the Great Sword that has disappeared.

A decorative string was hung on the central weapon.

It was a decorative string commonly called a susil.

Why on earth do you put water decorations on weapons?

Is this the same as hanging dolls on a bag in the hometown of Qing?

Of course, there are uses for that too.

Because the fancy water chamber indicates the level of the weapon.

It was absolutely essential for style.

However, this will always be a secondary factor.

The water chamber was originally a tool for training.

If you swing the sword with the right amount of force, the blade will extend in the opposite direction of the blade.

So, by carefully observing how your body moves, you can easily correct your posture.

When the teacher, the four brothers, etc. look at it, they can clearly see where the flaws are in each plant and branch, so it's good for sharing teachings.

And one more thing.

The water chamber also indicates affiliation.

If you have the seal of a famous and prestigious clan of a large sect, you can exert the divine power to subdue your opponent without even drawing your weapon.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After eating breakfast, putting on makeup, and leaving the house, the wind was really strong.

It's an amazing miracle of nature that rain pours up from below and hits your face even though you're wearing a raincoat.

Of course, that doesn't mean that strong martial artists can't go their own way.

It's just, ah, if you go to the mountain, it'll just be a mud field.

And it's raining, was it possible to stay overnight?

The idea that the wind was less blowing now because the old mountain surrounded Sangjanghyeon like a crescent moon was something that was beyond Qing's ability to begin with.

It could be said that this was a very high-level thought that's too harsh to expect from Qing.

Aside from the constant spray of raindrops on my face and the chin strap of my raincoat tugging at my chin, walking in the rain was surprisingly pleasant.

The sound of raindrops hitting each other.

This was because the dam was still functioning as a new one, and in technical terms, it's an 'impenetrable' dam, so rainwater does not seep through and it does not get wet.

Rain that doesn't suit me was cool.

The group arrived at the western foot of Mt. Mount Lao.

Rather, it becomes much easier to control your body.

The forest acts as a windbreak, so the wind only shakes the poor trees.

The rain that keeps pouring down from below was having no power as it first knocks down the leaves above before coming down.

So, first, we take a look around and slowly dig towards the highest peak of Mount Lao, Geobong.

But, as always, aren't there some rough guys blocking the road?

Despite the bad weather, it's admirable that he made the effort to find a magician and sell it.

Even if you say you're looking for a magician, it's not like your fortune will bloom, but rather you'll end up ruining your own life. What on earth was so great about these passions?

While the group quietly crouched in the bushes, Qing cautiously advanced alone.

"What's that over there?"

"Eek. I, I, I'm going to pick cornelian cherry trees."

"What? Are you a hunter?"

"Is that a woman's voice? Why don't you take off that thing over there?"

"yes yes."

And then voila.

The two guys' eyes open wide.

And then they look at each other and exchange sinister looks.

As the two men approached, Qing flinched.

"Why, why are you like this?"

"Why are you doing this? What else was there for a man and a woman to do together?"

"Please, the child was sick. He has a fever."

"Ah. So you're a woman with a child? Then you know what it's like to be a man. Don't you know the saying, "The more urgent the situation, the more you should turn back?" Rest for a moment and then go."

"After you rest, you'll forget all about that little brat. I'll send you to paradise."

"Huh, what kind of paradise was this? I'll send you to paradise with a skewer like a tree branch."

"What was it? Did you see it?"

"You see, then. I almost pulled it off, thinking it was some kind of earthworm. But I held back, thinking it might be one of yours. It wasn't until the urine started squirting out that I finally opened my eyes."

"Even if that son of a bitch says something."

The Qing court made its decision.

You said you came to get medicine because your child was sick, and all you do was snicker and make obscenities?

Yeah. Death penalty.

If I live, I guess the only thing I regret was the air I breathe.

In fact, this was a malicious entrapment investigation.

A cloudy day with rain falling. In a deserted forest.

A lowly woman who can be touched without any repercussions.

But isn't the color unusual?

Even for a naturally decent person, wouldn't this be the perfect situation for dark desires to blossom?

Especially if he was not a decent person by nature.

Of course, he did not tempt Qing to commit a crime.

But even with makeup on, her face itself was quite alluring.

You could say that the man was trying to cross the line, or you could say that he wasn't.

"I, that, the great swordsman. If you do this."

"Ugh. Great swordsmanship. Great swordsmanship was good. But I'm the only great swordsman, and that guy was a small swordsman."

"Isn't this kid doing something right?"

"I'm sorry. But you can't call something small something big, so just kill me."

"That fucking kid……"

"Whoa, whoa. You go first."

"You jerk."

"Of course the smaller ones should go in first."

"Pfft."

Miss, how can you put up with this?

It's a truly remarkable talent for killing.

But the joke was so natural that it's not something that's been done once or twice already.

If I had been a jokester with that gift of gab, I would have been famous all over the world. Instead, I ended up living like a bastard and getting stabbed to death.

"What? Are you laughing? You bitch, aaaah!"

Yay. Heavenly Demon Ray.

A black line shoots out from Qing's finger.

A thin, narrow beam of light touches the ankle of the small man and causes a small explosion.

The Tathagata Goddess, ring the bell. The bell was ringing so majestically that it's useless.

Because there are only so many long-range attack methods that can be easily projected.

Of course, the power was also poor.

It looks like the small business man was at his peak.

At that point, the explosion of the Heavenly Demon Ray was just a pure physical force, so I grabbed my foot and jumped up on one foot.

"Huh? Huh."

The sharp blade of Qing's hand falls upon the man who has lost his cool.

Blood spurts out from the great swordsman's nose.

Oh. So this was a really possible skill.

While Qing was admiring him, the Sohyeop man quickly draws his sword.

"You bastard! You lied about your identity!"

In response, Qing points her finger at the man's back.

"Oh. There's someone behind you. Be careful."

"Huh! Who would be fooled by such trivial tricks!"

"You really lack trust."

"How dare you touch the Yongcheon Twins!"

Pfft! The small-scale gangster who got hit on the back of the head collapsed with a thud, his legs giving out.

As his consciousness fades away, the man desperately turns his head and sees a middle-aged man holding a thick wooden club.

"Ugh, I got fooled. I didn't think it was real……"

And then the iron fist.

Of course, passing out doesn't mean your life in the martial arts world ends.

And just because someone was funny doesn't mean they'll let them go.

If people would let it slide just because someone fainted or was a funny guy, the martial arts world would be a much warmer society than it's now.

The suffering of Yongcheon Ssangsal has just begun.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Mount Lao can be broadly divided into four areas.

From the point of contact between the valley that cuts through Mount Lao diagonally and the Baeksa River that divides it into north and south, Bukak was to the north, and Dongak was to the east.

And the area around the waist where Jeilbong, Jeibong, and Jesambong are all gathered, and Nam-ak, which rises along the southeastern coastline below.

The area where the Qing party was active was right west of Nam-ak.

And it was also a place where the lives of the vicious warriors who had come to Mount Lao in pursuit of the small hope of the fierce and evil magician of the world were lost in agony.

Of course, not everyone lost their lives.

"I have to find the cornelian cherry tree…"

"Kekekeke, hey, you bitch. Do you know who I am? I'm none other than the non-human spearman, Bansalta. Do you have any idea how many lives have been lost to this spear?"

"Ugh. Please, Great Expert, the child was sick…"

"Hehe, why are you shivering like that? Do I looked like I'm gonna eat you?"

"Then this girl is off-"

"haiyaa. This girl was such a worthless bitch. Where are you going? You can't go."

"But, the child-"

"This bitch. Don't you know that this mountain is full of vicious bastards right now? If your child is sick, you should go to the doctor. Why are you, a foolish woman, looking for cornelian cherry trees and falling down like that? You can't just get out of here?"

"But-"

"You bitch! If you have a kid, you have to be even more careful. If you die while looking for herbs, both you and your kid will die. Get out now! Or should I make you die quickly here??"

\textit{What the heck? Is he secretly a nagging grandma?}

Anyway, it's a disqualification for the beast.

"Voila. You've passed the human test. You can now leave Mount Lao."

"Huh? What?"

"Now, look here. It's sparkly."

Today too, it's a little star that twinkles brightly.

The face of the non-human bastard was distorted.

"What are your intentions?"

"Hmm. Isn't this enough? Then look over there. It's sparkling."

Tian Yuxue sighs deeply and lifts Kang-hwan up.

It was not the starlight in one's hand, but the starlight that Kang Hwan, a real star that has risen to fame, emits.

Only then does the color drain from Bihyeongdanchang Bansalta's face.

"Ugh, the deceased, the deceased-"

"The word 'deceased' was always a bit tricky. Hmm. Anyway, he seems like a bad person, but this isn't working. Why don't you just leave instead of hanging around in the magic world? Isn't it too dangerous with all these strong-willed people like me all over the place?"

"Leave, I will leave."

"Live well. That's why I'm saving you."

"I will live a good life."

I saw the evil deeds of Bansalta leaving Qing.

This kid was so lucky.

Maybe you were reminded of your difficult childhood with your mother, or maybe you just miss your mother.

Anyway, thanks to that, I saved my life.

The next survivor was also peculiar.

He was my child, my husband, and I will treat him well, so why don't you get married?

Hmm? Isn't it ambiguous?

The decisive factor was the appeal that if he promised to get engaged, he would raise the child as if it were his own.

A pure and innocent man who barely passes the human test.

At that, Tian Yuxue clicked his tongue and shook his head.

"Well, disciple. I need to touch up your makeup."

"Huh? Why?"

"Come to think of it, isn't it a problem if your beauty was too outstanding? Men are creatures who inevitably follow that path down there, so isn't it more like throwing out bait?"

So, by adding things here and there to the face, I made it into an eaves.

The next guys I met were like this.

"Damn, you've lost your eye. You're just ruining my mood. Ha, you're ruining my appetite. Hey, do you know your way around the neighborhood?"

"I don't know much about you, but you're looking for cornelian cherry, Miss. What kind of bastards are you? Swinging a knife while someone speaks? I can't forgive you! Don't you even have a mother? You failed! In the name of your mother!"

Anyway, whatever a savage does, he'll end up dead.

When she's pretty, he tries to knock her down, and when she's not, he swings his sword as if he's seeing something dirty. Either way, the human nature of the villain was extremely cruel.

Human fails. Beast passes.


\vfill
\begin{lstlisting}
	Yet another line in K-drama Iris (아이리스)
	
	This was the full dialogue:
	
	Hyunjun: There was a sad legend about this statue.
	Seonhwa: What… a sad legend?
	Hyunjun: …
	Seonhwa: What kind of legend was it?
	Hyunjun: I don't believe in legends.
\end{lstlisting}