\chapter{I don't believe in legends (5)}

Yangsiwon, a small restaurant in Heilongjiang.

A strange, refreshing, and bitter aroma filled the table with dishes.

It was the unique scent of a vegetable called hyangchae.

However, hyangchae was a vegetable that people either like or dislike.

Those who like it will go crazy even if it's roughly mixed with oil, but those who hate it will frown at even a small leaf.

The guests were averse to it and even politely requested that the spices not be added.

however?

"If there are no spices, it's not Northeastern cuisine. If you're in the Northeast, eat Northeastern food."

I even asked them not to put it in, but they insisted on putting it in and are talking nonsense.

Of course, for the sake of the pride of Northeastern cuisine, they may have added spices that they didn't necessarily put in.

Or, as I was making it the way I was making it, I ended up adding it naturally out of habit, but I may have pushed it forward because I thought it would be a waste of money and effort to make it anew.

It must have seemed easy, since it was an unarmed grandmother and two women who looked like her granddaughter.

But now we can't know if it's true or not.

"Krrrr……"

Because the maid was lying on the floor with blood foaming in her mouth.

I'm writhing on the floor with a hole in my stomach after being hit by a real minority witch's real minority magic.

The monk dies because he put in spices that he was told not to put in.

However, anyone who dislikes spices would probably think that they have committed a mortal sin.

For reference, in the hometown of Qing, this spice was called coriander.

As the blood of the deceased spreads on the floor, the minority group stirs the food on the table.

"Tsk tsk. How come there's no place that nasty weed hasn't gotten into. Tsk, Chuguya, it's useless. That's not how you eat it."

A very ugly dog ​​tries to lick the blood, but was stopped by the minority's threats, makes a sad sound, and covers its eyes with its front paws.

A rare smile appears on the face of the minority believer.

Then, a plate of fried rice floats up and lands in front of the dog.

It was a sophisticated technique of attack and subjugation that only the best among true experts can do.

Then, it starts eating happily, making the characteristic grass-eating sound of a gnawing dog, and sticking its head in.

Shinpa stares blankly at the sight, then crumples his expression again at the rising scent of coriander.

"Don't you Northeasterners have anything to eat? Why do you eat things like this?"

"If you drink Corul, you'll only be able to muggle."

It was Yun Yuanying who had pinched my sharp nose with tongs from somewhere.

The minority group clicks their tongues at him.

"Do I really have to eat that much?"

At that, Yun Yuanying smiles and takes off the tongs.

"Still, this Tangchoyuk was fine. Oh my, this one has a rather unique flavor, doesn't it? Shinpa, ahh."

"Get rid of it. The smell of that damn spice was completely ruining my appetite."

The minority group was still angry, so they pour out the steaming miseon (noodles made with thick noodles from the Northeastern style) on the floor.

On the floor, there was a monk who was dying for the sin of putting coriander in the water, so he was screaming and spitting out blood after pouring hot soup over the hole in his stomach.

Unyeonyoung nods at him, then suddenly says something out of the blue.

"That's right, I'm planning to go to Mount Lao."

It seems like he went to a nearby mountain.

"Huh? Mount Lao? Is there a mountain like that nearby? The only Mount Lao I know of was the one over there in Sandong."

"That's right, Mount Lao."

The melodrama's expression was bitter.

"No, the grand plan was coming up soon, so where are you going? Those Malgal guys are making a big fuss, asking when the hell you'll get anything done. If you go, who's going to call the jiangshi?"

"There's something happening in Kyo-ga No-san too, isn't there? It seems he's overwhelmed, so the old man from Gwisan Man-bak was begging for help."

"Well, what kind of work can an old man who only knows how to tinker with machinery do? Just leave him alone. When will he ever get to that distant mountain?"

"Even if I try, it's only 4,500 li at most?"

"Usually, 4,500 li was not considered the maximum."

"If you go a thousand miles in a day, well, it won't even take five days."

"And you're going to ride in that bizarre coffin? And you're saying you'll be locked in there for five days?"

"Oh my, a coffin? It's a bed.

Bed carriage. It means a bed carriage.

But to the minority, it just looks like a big coffin with four handles.

When you look at the four of them running in the bloody river, no matter how you look at it, it looks like they are carrying a bier, not a palanquin.

"Besides, I just need to lie down and sleep, so I'm locked up."

The blood dragon does not sleep, does not eat, and does not get tired.

It means that you don't sleep or eat for twelve hours a day and just run all day long.

Of course, if you run a thousand li a day, the price you pay for it will be the lifespan of your four blood vessels.

It's like pouring in the Blood Cult's wealth to create a Blood City, only to be consumed by rapid movement.

But the price was something that the dark dragon who asked for help has to pay, and there was no need for Yun Yuanying to worry about it.

Didn't Yun Yuanying clearly ask that?

Do you really want to help?

The minority group has a displeased expression.

"Tsk. Why are you going to help an old man who can't even eat, let alone be kind?"

"Oh my, but shouldn't we help each other as members of the same bloodline?"

"Anyway, tsk. These guys don't know how valuable they are, and they're just using them like that. When are you going to leave? Wouldn't it be better to just quickly get rid of those guys and go with them?"

"If you're with me, wouldn't it be impossible to travel a thousand miles? Can you lie in bed for five days, eating only rice balls?"

The expression on the minority's face suddenly turns sour.

After lying down for five days, eating and sleeping, how could an old woman like her want to be put into something that resembles a coffin?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

I roughly walked around Mount Lao Mountain.

This means that the chain of resentment of the innocent but sinful Sapa bastards has also come full circle.

According to the information that everyone has vomited out like a will, it seems that they haven't even found a shadow of the magic absorption technique, let alone a trace of it.

There was information that a very suspicious cave had been discovered.

However, as marked on the map that Tian Yuxue borrowed without the owner's permission, it was nothing more than a natural cave that originally existed.

There are two signs warning that if you go too deep, you won't be able to get out.

There are probably still Sapa people wandering around in dark caves, starving to death.

It was a treasure hunt that lasted ten long days.

It was not known when treasure hunting began to refer to the act of raiding to gather information and then framing others to spread discord.

This isn't a treasure hunt, it's just a complete mess.

So I decided to take a break for now.

The Sapa guys are now focused on protecting themselves by sticking together as treasures and such, so the search was on the back burner.

On the one hand, he was so anxious about how to stab him while sharpening his sword, so he judged that even if he left it alone, the absorption magic would be discovered right away and he wouldn't do it.

So, back to silence!

The Qing party stayed overnight for ten whole days.

Anyone can see that it looks like a real beggar.

As the group crossed the city, there were groups of people who looked at each other with suspicious eyes and followed secretly behind them.

It seemed like they had just climbed and come down from Mt. Mount Lao, so they wanted to ask about what happened during the hike, even if it meant using some extreme methods.

But the stalking soon ends.

Because the Qing party would naturally enter the Mount Laoru, the first guesthouse in the Imjeokjeil district.

Even with that appearance, he goes to the most expensive and top-class guesthouse in Mount Lao as if he were completely accustomed to it?

Well then, I guess we're not the ones to mess with.

In the first place, those who remain in the immediate vicinity are in the process of protecting themselves, so if the opponent was unusual, they are quick to give up.

Those who survive have a reason for surviving.

Of course, not everyone who followed the Qing party gave up.

So, one of the men who had been following the Qing party, with wary eyes, carefully looked around and then entered the inn.

As soon as Qing enters the guest house, Jeomsoi runs out.

Of course, the point of the most delicious restaurant in Jeommokjeilgaekjan was the same as the point of the most delicious restaurant in Jeommokjeilgaekjan.

At this point, you need to have the wisdom to not judge someone just because they look like a beggar.

It was not too late to beat a beggar and drive him out after it's clearly revealed that he was a beggar.

You might say that's not even wisdom.

Many people in Zhongyuan suffer because they fail to realize this very simple wisdom.

It was like that yesterday, and it will be like that today and tomorrow.

"Nari, what do you need?"

"The best room. And the bath. Now."

The blue hand draws mysterious movements.

The hand that had dug into the sac with the Muyeongshinsu moved unseen, and something yellow and brilliant jumped out.

The arm of the person who accepted it without thinking suddenly goes down.

Because gold was heavy.

Jeomsoi gulps at the brilliance of the pear-shaped gold nugget, Geumwonbo.

If someone saw me, they might ask why I brought such a heavy gold ingot when I was going to climb a mountain.

There wasn't one when I entered the mountain.

But it comes out.

Strangely enough, it was a golden nugget that appeared somewhere along the way.

In fact, there are Divine Thief and reserve Divine Thief in the party.

Can't you do this level of magic?

"I'll get it ready right away! Hey, Jorang, invite the guests to the fire-breathing room! Ddungdungi, Daesik, and Cheojam, get the bath ready right away!"

Originally, the best rooms in the best inns in the city were named after the symbols of that neighborhood.

The name of the best room at the Jeomukjeil Guesthouse was Bulrocho Room.

This was because in the past, Qin Shi Huang searched Mount Lao with great care in search of the elixir of life.

Mount Lao has been a famous mountain known for its pure energy and beautiful scenery since thousands of years ago.

So, after ten days, it feels like I'm soaking in hot water.

"Haa……, this was truly paradise."

Unlike Qing, who took a couple of baths in rainwater along the way, I think the teacher and the children would have been very moved.

If it was going to be like this, shouldn't I have not washed either?

It's paradise if you endure it and endure it again.

After washing up like that, it was time for a simple makeup session.

Even after rinsing it thoroughly with soap, Murong-ju-hee, who had a fake breast that gave off a musty smell, looked extremely uncomfortable.

I guess it's the limitations of the material.

What can be done when the pig urine was old and has been exposed to rain?

For Murong-ju-hee, it was a ten-day period in which she felt the weight of the wealthy.

Fake breasts that are heavier than real breasts.

It takes ten days to wear it all day.

Half of my back, including my shoulder blades, back of my neck, and the muscles between my shoulder blades, were stiff and sore.

When I wake up, I have phlegm and it hurts to turn my head.

There's a foul smell rising up there that only affects me.

How on earth does the young lady manage to live with something like this? It's twice as big as this.

Since it was made for JinChangming, the size was adjusted to fit his body.

Anyway.

And only then do I drag my tired, melted body down to do some simple yoga.

The moment the Qing party appears on the first floor, the man who was sitting in the corner with his hat pulled down deep opens his eyes.

He was the one who followed the Qing party.

"Jeomsoi, what kind of food do you have here?"

These are special guests who came down to the light without any notice.

The moment Jeomsoi was about to take a deep breath-

"Just bring me ten of the best ones in order. Master, what do you want for dinner?"

"There are ten dishes, and you're ordering a meal?"

"Then, you don't order it even though you have four mouths?"

Qing looks back at Chen Changming and Murong Zhu Xi as if asking for their consent.

"I'm done."

"me too."

Of course, I didn't ask for consent.

So, Qing was upset.

This was really too much.

It's so nice to order different things and share them so you can try a variety of things.

Cooking was cooking, and eating was eating.

"Ugh. I'll have to eat alone. Jeomsoi, milk porridge, rice cooked in a pot with three kinds of vegetables, and some daechang choban."

It's a lot for someone who's going to eat alone.

But Jeomsoi wasn't surprised.

The guests at the inn are the same.

Originally, rich people ordered this and that, took a few bites, and then threw it away.

The most basic way to show off wealth.

So everyone was like that about orders.

I just thought the gold and silver were rotting away.

Yes, that's right.

It's too early to be surprised.

What if you could eat every last bite of a meal and dish without leaving a single bit behind?

Perhaps one of them will be so shocked that he will lose consciousness.

"Yeah, huuuup……!"

Then, the roar of the eagle bursts out.

The names of dishes are lined up one after another, with a loud voice like the roar of a Shaolin monk.

And the corner of the guest room.

The man who was hearing the scream slowly got up.