\chapter{I don't believe in legends (3)}

There was a saying in Qing's hometown that a single loach can muddy the whole pond.

In other words, it only takes one loach to muddy a pond.

Of course, a pond with solid rock or gravel that has pressed down the soil will not become cloudy no matter how much the loach twists its body.

For loaches to muddy the water, there must first be a lot of dirty stuff on the bottom.

So, was Sapa called Sapa for nothing?

They are the kind of people who work together with a cunning glint in their eyes, but who also try to keep each other in check and obstruct each other with the intention of taking more advantage of each other.

In a mountain where so many of those sects are gathered, they really start a fight to instigate discord?

The first-class warrior of Gangpaecheon opens his eyes wide.

When someone's hand was stuck in your chest, you can't help but automatically cry out even if you don't want to.

"Why, Seo……?"

"Why? Hehe. Are you asking because you don't know?"

The holy spirit of the fallen, Jun Ki-chung, pulls out his hand.

With a fresh heart clutched in his hand.

And then he squeezes it tightly and crushes it.

There was one gaze that's watching the scene from a hidden perspective.

He was the second-ranking disciple of Kang Pae-cheon.

It was absolutely not true that I hid because I was afraid of Taeshimanho Jun Ki-chung.

Someone has to survive.

Shouldn't I stay alive and report the attack by those evil Jeolnaksung guys to the main force?

Because it was an attack led directly by the Holy One of Jeolnakseong.

And if anyone had to live, it was me.

There was no need to particularly worry about why the Jeolnaksung guys do such things.

Originally, the ten great natures of the Apostles were a term that collectively referred to the five great heavens and the five great natures.

In terms of political dynasties, it would be around the Five Dynasties and Ten Dynasties.

That is, the five strong sects are called the Five Great Heavens, the five weak sects are called the Five Great Stars, and the two together are called the Ten Great Heavens.

Naturally, the Five Great Saints want to bypass the Five Great Heavens and take the title of Saint and attach the title of Heaven.

So, isn't this a scheme to wipe out the emergency search team of Kang Pae-cheon, whose strength was greatly reduced after being attacked by the Blood Cult?

Kang Pae-cheon's warrior holds his breath even more.

So you must not get caught even more.

In order to inform and prepare for this conspiracy, we have a duty to keep our eyes on our brothers who are dying now and report on it.

It's not that I'm hiding because I'm absolutely afraid or scared.

I'd love to go out there right now, swing my sword, cut down those vile bastards, and burn their lives to ashes, but I have to report.

It's really unfortunate, there's nothing we can do.

Oh, I see. Huff.

He was the disciple of Kang Pae-cheon who saved his life by suppressing his heartbreaking sorrow.

After the Jeolnakseong raiding party disappeared, he watched for over half an hour before finally running out to report the news to the main force.

"What the hell? Those damn bastards!? Why!"

"You're trying to bypass us now…"

"Ahem."

Elder Kang Pae-cheon groans in frustration.

Of course, that's true.

Since they've been running wild and causing a commotion in the city, it's only natural that rumors of a Blood Cult attack would spread.

I don't think it's a misunderstanding or slander.

Well, I guess they're finally showing their true colors now that they've come to attack.

And the same goes for misunderstandings and slander.

There was no need to talk to the enemy after Kang Pae-cheon's brother was brutally murdered.

So the two groups put the treasure aside for the time being, secretly lowered themselves, and began to bite each other.

Oddly enough, the madhus move around in groups.

Aren't they just the kind of guys who do things that are perfect for getting killed?

As a result, resentment grows and grows.

One was weak, but many are strong.

This was the reason why the madus are so sworn brothers and flock together.

These bad guys are called by different names depending on their neighborhood, number, and crime.

The most common one was the dog.

For example, Jang An Sam Gyeon, something like that.

These are the guys who commit petty crimes such as stealing money for drinks, harassing women, causing trouble at other people's businesses, attacking the elderly, and being rude and mean.

Strangely enough, the pride of the wicked was their evil deeds.

So, the evildoers of the level of Ken do not call themselves Ken.

It was humility to know that you are not good enough to call yourself a dog.

However, if you continue to commit even worse acts there, people will recognize you as Maduro and change your last name.

Those who are called ~~heungi are vicious criminals.

Those who are called ~~sal are serial killers.

Then, the evildoers will say with their own mouths, "We are the three evildoers of Chang'an, aren't we great?"

In reality, it's a kind of stigma that tells you not to associate with him because he's a terrible guy.

When I met several people in Mount Lao, I realized that Hyeong and Sal were just beasts who didn't need to take the human ability test.

"I just have a dogwood… My child was sick and has a fever…"

That damn cornelian cherry was a very expensive product to sell.

In fact, according to medical books, cornelian cherry has no fever-reducing effect.

According to the Yellow Emperor's Classic of Internal Medicine and Compendium of Materia Medica, cornelian cherry was said to be good for increasing male stamina.

It has no antipyretic effect.

But why on earth was the child looking for cornelian cherry when he was boiling with fever?

Since the child was already wrong, she says she can just have another child and was looking for cornelian cherry to feed to her husband?

The correct answer was that the roots of the Qing are the Korean people.

If you say it's a cornelian cherry fruit, then it's like that, right?

The desperate fatherly love of a father who waded through the snow to bring food to his sick child?

Of course, it's incomprehensible why the father would wander through such a cold, snowy, dark night to find a natural aphrodisiac for his feverish son.

"We are the elders of Yeogangyuksal. Hehe."

Yeogangyuksal? Is it flesh?

Qing's sad expression disappears.

"Oh. Really?"

Qing snaps his fingers.

Then there was a rustle.

Tian Yuxue, wearing the martial arts uniform of Jeolnakseong, appears with the two of them behind him.

The more diverse the means of sowing discord, the better, was Qing's wisdom.

Qing was only clever when he was making trouble for others.

"Who are you!? Gasp, Jeolnaksung! Why are the great warriors of Jeolnaksung doing this…?"

I thought the blue was really interesting.

Is there any common ground between the two?

You've managed to recognize all the martial arts.

Well, I can tell right away if I see the Gudaemun School uniform.

"You dare interrupt the celebration of Jeolnaksung. Pay the price for this with your life!"

Tian Yuxue speaks solemnly.

The murder of Yeogang Yuk was unfair.

What event did we interrupt?

Of course, if you feel wronged, you have to express it so that they will understand.

"What, what are we…"

Tian Yuxue smiles wickedly.

I thought that the expression suited Qing very well.

"Isn't the best way to monopolize a treasure to eliminate all competitors?"

At that, the strong-willed Yeogang Yuksal draws his sword.

However, Tian Yuxue responded by quietly lifting Kang Hwan up.

Yeogang Yuksal's shoulders suddenly hunched.

"Well, we're going to give up and retreat now-"

"No way. If we let those who dared draw their swords against Jeolnakseong go, what kind of reputation would we lose? Shouldn't we at least give up one place to make things more manageable?"

"Ugh."

"Well. Since you touched the daughter of Jeolnakseong, if you were to become women, you'd probably figure it out. Now, hand over your genitals and disappear."

The two men looked at each other with suspicion.

"That, sir? Or a regular finger."

"Amniotic fluid."

"Then, up to three fingers-"

"Amniotic fluid."

"Oh, that. I'd rather leave one wrist behind. Please."

"Amniotic fluid."

It can be said that this was almost on par with Mr. Lee's firmness in calling for a neutral country.

Of course, Chen Changming and Murong Zhu Xi, who were standing on the left and right behind Tian Yuxue, were observing Jin Chang, unable to bear to look ahead, with the tips of their ears red.

It looks a little cute to me.

Are you embarrassed by the sound of your penis?

It's not like I'm a kid.

No. Are they really kids because they're small?

"Do you think you'll end up like this? Strike!"

It was the beginning of a desperate struggle to protect the yang water.

Of course, I couldn't keep it.

"Haha, how are you? Are you feeling wronged? Are you feeling wronged? If you feel wronged, come to Jeolnakseong anytime, you girls. Wow, for a girl, you look very manly. Hahahaha!"

Yeogangyuksal, now Yeogangyukgoja.

Tian Yuxue slowly turns around, taking the medicine.

Qing follows, and Chen Changming and Murong Zhu Xi, who were waiting beyond because they could not show the dirty things, join the group.

The remaining female warrior, with her lower body stained with blood, gnashes her teeth.

I'd rather kill you!

What tyranny, what disgrace!

But, one surprising fact.

The archery style was not a Qing idea!

It was Tian Yuxue's idea.

Qing said that it would be enough to just wave a hand signal.

Then, as a villain, you will become insignificant and your resentment will be directed towards those who killed Jeolnakseong.

But Tian Yuxue shook his head.

If you cut off his wrist, he will be scared and hide, and take out his anger on innocent people.

So, if resentment was directed at the poor, the weak and the poor, it will cause more harm to the world.

So it's a palace.

Qing, you're not a man so you don't know (Qing was wronged, very wronged), but a man can never forget the resentment of his wife.

Even the great Sima Qian was castrated and castrated, and was unable to control his urination due to lack of support.

So, it was said that even close friends could not stand the stench and would not meet him.

So, the misery was indescribably terrible, and Jeolnaksung and I will become mortal enemies who cannot live under the same sky.

Wouldn't you become a vengeful spirit who seeks revenge even if it means burning your own body?

It's a terrible idea that a normal Confucian scholar would never dare to say.

Tian Yuxue also became very angry.

How many times have I seen villages annihilated?

Even without seeing it with your own eyes, it's obvious that other villages suffered the same fate.

Moreover, there was no one in the group who can stop this rampage.

Chen Changming preferred not to impersonate others and cause damage to the Shinnyeomun, and Murong Ju-hee was equally angry.

Like that, one day, two days, three days, four days.

The Iron Blood Sword Heaven's stronghold was attacked by Jeolnakseong.

The base of Choryubukducheon was completely destroyed by Cheolhyeolgeomcheon.

Gwangryongseong's stronghold was attacked by a special force from the Choryubukducheon and suffered great damage.

It was a case of resentment that went round and round.

There, the warriors of the Ten Great Apostles constantly raid small and medium-sized sects and become enthusiastic about eliminating their competitors.

Besides that, the many eunuchs who appeared sharpened their teeth toward the great sect of the apostles.

Some remain in the mountains and carry out secret raids to vent their grudges, while others retreat, hoping to return in the future.

If someone saw me, they would say that I came here looking for a magician and just kept picking fights.

However, it also serves as a treasure hunt.

But, do you really need to find it yourself?

If I could share the results with the guys I was looking for, I would think that even the bad guys would be able to do it, and that this mountain was not the only one.

As a result of this revenge, it was now possible to find the body anywhere on the mountainside without difficulty.

It was truly a struggle of all against all!

If you quietly climb the ridge, you will hear the clash of weapons, shouting, "Die! You enemy of the Socheonju! Who do you dare to touch!"

Just four villains can cause a sea of ​​blood throughout the mountain.

It's like saying that one loach can muddily up the whole pond.

but.

It was the law of the world that after a loach muddies a pond, the water becomes clearer.

This was because the slippery mucus unique to loaches firmly holds onto floating objects and causes them to sink.

So, isn't this tragedy of evil people killing each other a truly heartwarming sight to see in the world?

