\chapter{I don't believe in legends (2)}

Creating a hell for the wicked.

Materials. Villains. The more the better.

One. Please cut the ingredients into large pieces.

It was best to crush the limbs, but it's better to avoid self-imposed dislocations.

(You can enjoy a quiet hell of wickedness by drilling a hole in your throat.)

Two. Please dig the ground.

Since the materials are decorative, you don't have to dig too deep.

3. Once the ground was dug to a certain extent, put in all the prepared materials and the hell of the wicked was complete!

You can enjoy it by teasing and teasing it according to your taste, or you can throw rocks, stab it with a spear, or just go in and roll around for a while to make your broken limbs feel the pain.

The recommended method was the so-called 'Do you get the general idea?'

From now on, kill each other, and I will spare only one of you.

You can also enjoy the spectacle of wicked people who are dissatisfied with their limbs, tearing at each other with their teeth and crushing each other with their bodies, claiming that they will live alone.

Of course, it won't do any good if they just help each other anyway.

"Hmm."

I have summarized the production method of Qing.

We should leave this behind as a secret and pass it down to future generations as a method of executing evildoers.

But if it falls into the hands of the wicked, it will cause great harm to the world, so it's a pity, but I will quietly remember it.

It was truly heartbreaking that there was a woman's body.

If it were a man, I could have watched him pee his pants and run away in terror.

Of course, there's nothing a woman can't do.

But what's there to make a spectacle of?

Those guys will never look good.

It was a dark evening.

Even with the blue human's superhuman vision, it's still clear enough to see, but for someone with poor night vision, it's already impossible to see anything.

Qing looks down into the pit with cold eyes.

Half a sheet?

It was a shallow pit where the ground touches the tip of your nose when you stand below.

Of course, once all of your limbs are crippled, that class will be seen as an insurmountable obstacle, like a cliff a thousand feet high.

Qing stares blankly at the floor overflowing with reddish yellow mud and blurts out a word.

"I hope the soil drains well. Still, there are quite a few of us, so if it feels like we're going to drown, can't we just drink it all up? They say yellow clay was good for you, after all."

For the Korean people, yellow clay was a fearsome natural panacea that they use to spread it on the floor, apply it to the walls, and even make pillows and pillows out of it.

Hmm? But?

Come to think of it, the word 'yellow clay' was also funny.

Why was that yellow? Isn't it red?

If you look at the real red soil of Qingdo, you will think, "Ah, so that's why they call yellow soil yellow soil. Real red soil was really red."

In fact, Qing's doubts are natural.

The people of Zhongyuan had never seen red soil, so they did not know that a redder soil existed, but they insisted on calling it yellow soil.

Why was that?

In fact, it's loess because it's just land, whether it's brown, black, or even flesh-colored.

The yellow sword that presses the current.

The color of the sky was black and the color of the earth was yellow. The end.

This was exactly what Qing thinks when he looks at the villains struggling in the mud.

Qing turns around and heads towards the cliff that's about four meters high.

The rocky mountain also had its own advantages: the jagged rock surface provided several shelters from the rain.

"Can we light a fire soon?"

"Yeah. Do you know how to make a fire in the rain?"

"Hmm. A stronger force?"

"Okay. Take this opportunity to watch and learn."

Rocky mountains are usually covered with pine trees.

And it's difficult to survive on the coast without salt-resistant pine trees.

Then what about Mount Lao, a rocky mountain attached to the sea?

"Pine wicks burn well even when wet. This place was full of pine trees, so you'll find pine trees as soon as you pick them up. But on other mountains, it's better to look for pine trees."

Then, he rummages through the pile of firewood he has gathered and takes out a large lump of pine sap stuck to it.

"The more rosin a stick has, the better it burns and the longer it lasts. Who picked this up? It was picked up really well."

Tian Yuxue peels off the shell.

Then he dug out the wick and sliced ​​it thinly with a mallet, making it flutter.

After that, when the igniter was brought in, the wet wood quickly bursts into flames, making it colorless.

Throw a bunch of shells there.

If you cut other firewood into thin pieces and put them upright.

The bonfire was ready in no time.

Of course, it looks easy because Tian Yuxue was a master of Hwa-gyeong.

Isn't he a master who can chop a piece of wood into pieces as if he were slicing tofu?

Moreover, since I am used to it and familiar with it, it seems like the work that a craftsman does was done carelessly and haphazardly.

"oh."

"But, oh, gulp, it's wet wood, so it's not good to smoke in a confined space."

It was a hollowed-out terrain between rocks that's difficult to call a cave.

The thick smoke billows upwards, drifting out through the ceiling, but its aftertaste lingers, stinging your eyes and making your nose tingle.

I was wondering if it was okay to light a fire, but the teacher said it wouldn't be a problem.

It's deep, with cliffs above and forests in front, so it's rare for anyone to come here after seeing the light.

It's also dark, so you won't be able to see the smoke rising, so you won't be able to identify it from far away.

I lit a fire and roasted the deer I had caught earlier, strangled it, and hung it up.

Although the smell was a bit strong, I have a strangely generous appetite when it comes to eating out.

And then I hung up my wet clothes to dry, changed into spare clothes, and lay down to listen to the sound of the rain and chatted about useless things.

However, the floor was made of hard rock, so it's quite uncomfortable.

Of course, Qing still sleeps well.

Because he was not a great man who would get hurt even if he slept on a gravel field rather than a stone floor.

However, Chen Changming and Murong Ju-hee are very uncomfortable and seem to be tossing and turning, unable to sleep.

How often would the two of them have to sleep in the wilderness?

Chen Changming was quietly training at the Shinnyeomun.

Murong Zhu Xi, a descendant of a noble family, always stayed at the best inns when he traveled, and he never had to light a bonfire on the street.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

One of the laws of Zhongyuan.

If you follow the river, you will find villages in remote areas that seem like they would never be inhabited.

Of course, this was the law of Zhongyuan, so the border areas are an exception.

The border was a river, a valley, and unless it's a city, no one lives there.

In any case, according to this law, it's not particularly surprising that there are villages around the small valleys in the upper reaches of the Seosa River, which flows between Nam-ak and Jung-ak in Mount Lao.

Because the history of Zhongyuan was a history of corrupt officials exploiting the common people.

So, people who were more afraid of management than wild beasts that attacked people, such as tigers, wolves, and bears, hid in the dark land.

And what if we add to that the closed-off village culture unique to the Chinese people?

Around the waterways of the Jungwon Mountains, there exist uncivilized rural villages that look just like the scenery from two hundred years ago.

The village that the mountaineers called Jukwachon was also such a hidden village.

It was a village.

Until he became the Mount Lao branch of Jeolnakseong, one of the ten great natures of the Apostles.

The tragic incident that struck Jukwachon, a village hidden among bamboo groves as its name suggests, was the result of a combination of several factors.

It was also because he was threatened with a knife and confessed the location of the village, not knowing the kindness of the mountaineer who had allowed him to stay while hiking.

It was also due to the carelessness of the people of Jukwa Village who exposed their location by lighting a fire even though it was well hidden.

Of course, even so, the blame for this tragedy lies entirely with the Jeolnaksung unmanned people.

He was the one who started the village cleanup, saying that a good base had been created.

Thus, when the Jeolnakseong Seongjon Jun Gi-chung himself wandered around Mount Lao in the rain and came back empty-handed, he was able to fully understand the feelings of the people of Jukwa Village.

"Prodigal son, prodigal son!?"

Junki-chung jumps among the corpses of saints displayed in the center of the village.

And then, "Eaaaah!" He lets out a heartbreaking scream, expressing the pain of the captain in a Chinese-style expression, as if his intestines were being torn apart.

By the way, the word 'danjang' was a word that expresses the sorrow of parents who have lost a child.

That was exactly how Jun Ki-chung felt.

Because the body of Junwootang, the mortal son of Jeolnakseong, was there.

The bones of his entire body were crushed, his limbs were rolled up into a ball, and he was tied up with rope.

Looking at the bloodshot eyes, it would be easy to guess that the process was carried out alive.

You might ask why I sent my child to find the magician.

Well, I never imagined that anyone would dare to touch Jeolnakseong.

This lack of imagination, or what was sometimes called a safety insensitivity, cost Jun Ki-chung his son.

In fact, there were quite a few successors of the Sapha sect in Mount Lao.

Because there was a martial arts competition held by the Heretic Alliance, and it was natural for the successor to be present at such events to build connections.

Then, after hearing the rumor about Shingabibo, he quickly escaped midway, so wouldn't he have left the advance party to his successor?

Since the leader of the group takes credit for any achievement, it's also an opportunity to give strength to the successor.

"What kind of guys are they! What kind of guys are they! Aaaah! Find them! Find them now! Find them and bring them before me!"

But the rain was falling and the sun was setting, so what kind of search was this?

Jun-gi-chung just sat down on the floor and looked at his son's body.

The disciples, or in Jeolnaksung's terms, the saints, carefully watch the face of their sect leader, or in Jeolnaksung's terms, the saint, and collect and remove the bodies one by one.

That was when.

"Your Majesty."

Junki-chung's head suddenly turns.

The elder who spoke to him, who was the highest ranking, flinched.

Among the flowing rain, traces of blood and tears were clearly visible, spreading to the left and right of his nose.

If Qing saw this, she would say she would be so happy that she would die. If there was just one bowl of rice here, no, one bowl of rice? She would even go down a whole pot without any side dishes.

You killed other people's sons and daughters, and now you're crying tears of blood just because your own son died.

Can't the snow just melt and flow?

"My son, my son was dead."

"Well, I think you should see this."

What the elder held out was a water bottle.

Jun Ki-chung, who had hastily snatched the arm away, looked at the end of the handle of the sword and the thread attached to it.

A somewhat familiar shape, and on the octagonal piece of wood strung along the way, there was a single word: River.

Junki-chung turns over a piece of wood.

There's one letter there too. A thousand.

"Gangpaecheon……! Where did this come from?"

"Oh-hu-sam, the third-class star also came out of Oh-hu-sam's hands."

A spark of naturalization blooms brightly in Jun Ki-chung's eyes.

"These kids, how dare they."

"Your Majesty, please calm down. This could be a plot to sow discord—"

"What kind of sowing discord was this! Didn't you just say you escaped from the clutches of the saints? You must have held him tightly to leave the identity of the villain behind! Even as you lay dying! I demand vindication of my injustice!"

"but-"

"Yes, those Gangpaecheon guys have settled on the west bank, right? I will personally ask those Gangpaecheon guys the truth."

Suddenly, lightning strikes.

Junki-chung's face became whiter, and the shadows became darker.

A maddening expression was etched into the elder's eyes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At that moment, the Qing party was silent.

How many villages were there in the mountains?

How many civilians must have died?

I saw the corpses of the villagers roughly piled up and thrown away in the field.

So no one hesitated to touch another one of the ten great natures of the Apostles.

However, since I killed that guy called Successor, I decided to take it easy tonight and didn't even light a campfire.

In the dark night, no one speaks.

Then suddenly, Qing suddenly gets up from her seat.

\textit{Why should we be upset when we killed a bad guy?}

One must be confident in what one has to do.

Qing shouts loudly to change the mood.

"I can't stand it, it's so stuffy and uncomfortable! Let's wash up!"
