\chapter{I don't believe in legends (7)}

When Qing told her story, it somehow becomes a bit more intense than the original incident.

Of course, it's not unique to Qing, it's the nature of people.

So, there's no particular reason why one would put gold on one's face.

But this time, she didn't bother to mention the details, so the village was just wiped out, and I couldn't just stand by and watch the Sapa guys.

"Well. Even so, pretending to be a member of the Blood Cult and using the sect's symbol to commit treason? That's cowardly, Sword Friend."

"Huh."

Qing frowns.

This kid?

What are you saying after I told you so much?

But Nan-gong Shencai was confident.

"Those Sa-pa bastards always open their mouths and say that martial artists are nothing more than sword-wielding bandits. But then why was it that one side calls itself the Righteous Sect, and the world readily accepts it, while the other Sa-pa bastards, though they're afraid to speak to their faces, point fingers and curse behind their backs? Do you know what the difference is?"

"What was it?"

"That's because the sect members take responsibility. A robber with a knife? That's possible. But at the very least, a sect member should reveal his name even if he commits robbery. At the very least, willingly bearing the consequences of my actions, and even the resulting resentment, was the spirit of the sect."

"Hmm."

The original morally correct words are lethal.

There are many things to say in rebuttal, but the moment they are said, they instantly turn a person into trash.

Did something bad? That's not right.

There was something called morality in this world.

What would you say in response to this?

Does everyone else live like this?

That might be true, but are you really going to keep and live by each and every one of them?

If you're not careful, it really goes by in an instant.

He, Qing, Chen Changming, and Murong Zhu Xi all looked at each other with angry expressions.

Tian Yuxue slowly averts his gaze.

Nan-gong Shencai asks with a smile.

"So, let me join in. Where do you plan on hitting next?"

"Huh? I've already taken out all the guys who could fight. Treasure hunting has been put on the back burner because of the fighting, so I came down here to do some cleaning up."

"So, when will the maintenance be over? Why did you guys have such a satisfying experience among yourselves? Um, Namjae was a very overused alias. Would Sword Friend give you one?"

"……Didn't you just call me a coward?"

"I like being cowardly, too. Those Sapha guys are always cowardly, so why should we respond with dignity?"

"……? If that's the case, then why didn't you say anything, um. No."

How normal was it from the beginning?

The character '검치' in '검치' means 'fool' or 'idiot'.

Even when I'm engrossed in swordsmanship, I hear the sound of swordsmanship, so how much more so when I'm talking about non-swordsmanship?

"Hmm. Since it's already made a full circle, I'm going to watch for a bit and see how it goes."

"Oh, man. Looks like I'm too late."

Nan-gong Shencai made a regretful expression.

But that too for a moment.

Nan-gong Shencai, who had quickly regained his composure, stood up from his seat and spoke.

"Then let us do what we must do."

"Huh? What? What should I do? What's going on?"

Then, Nan-gong Shencai answered with a smile.

"Well, since we're two swordsmen, we should definitely spar. Have you made any progress lately? I've also had some enlightenment, so now it's time for us two super-swordsmen to get together."

"Oh. Super climax? Now it's finally starting to feel a bit rushed."

Chen Changming and Murong Ju-hee, whose ranks did not match, felt very disappointed.

Of course, the actual match never happened.

"You. Please grow up. I even gave you a disguise so you wouldn't be noticed, but are you really determined to become the spectacle of the whole town?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Book of Fortune, or rather the chain of grudges that created discord, was too powerful a stimulus for the people of Zhongyuan.

Because for the people of Zhongyuan, resentment was a debt that must be repaid unconditionally.

If you don't repay a grudge, the whole world will laugh at you and call you a child. (That can happen even if you're overly generous.)

So, it's only natural that he should avenge his brother's death at the hands of the neighboring Sapha gang who suddenly tried to eliminate his rivals.

But the grudge should have just been let go.

The seven sects of the Apostolic Ten Great Heavens fought each other's backs, fighting fiercely.

Then, at some point, you start to feel a huge threat.

If we keep fighting like this and the political bastards come rushing in, what will we do?

Aren't we just fighting amongst ourselves and only the political faction members benefiting?

Let's stop this and call a ceasefire while we have a common enemy!

Of course, the political party was just an excuse.

There was confidence that the political factions would not attack first and start a war.

This was because, while the Sapas hate the Jeongpas so much, they also have great confidence that the Jeongpas are upright and honest.

The real reason was that if they continue to fight like this, shouting 'Never again war', the power of the sect will weaken and they will fall out of the Sado Ten Great Heavenly Clans.

It's a shame to hold a grudge.

But it cannot take precedence over the sect.

It was a magnanimous decision, even though the grudge included the sect's grandson and his successors.

In this respect, the Sapa leaders are said to be much more responsible than the old, big-eared royal bloodline Hosooin.

Just because his brother died, he didn't commit suicide by abandoning his family, his subjects who trusted and followed him, and the people he pretended to care for so much, and throwing himself into a losing battle.

(Or maybe it was just a matter of priorities. Brother >>>> Subject > Citizen >>> Horse > Child.)

Thus, the intersection of the river and valley that divides the center of Mount Lao's Bukak and Seoak.

The leaders of each Sapa search party gathered.

Absorption magic was a very important matter.

So, the people in charge also have high ranks.

The elder, the previous supreme elder, or the lord himself stepped forward.

Of course, the gazes of others looking at the two lords are not very kind.

If you are the head of a clan, you must have a heavy butt.

How dare you come into this situation without any sense of dignity and put your head in it.

We also have Moon Ju-nim. This medicine was a bastard.

However, he held back for fear that if the Lord of the Moon stepped in himself, it would lead to a big problem.

Or the Apostolic Union itself will take action.

I'm afraid that the political bastards will come in droves.

But how can they be the only ones who are so lethal that the Lord himself steps forward?

Of course, I didn't just think about it.

"Your Majesty, you are truly diligent. Leading your men personally to such a remote mountain village. As the head of a clan, you must be very busy with your work."

Hey kid, don't you have anything to do?

"Isn't the true leader someone who stands at the forefront with agile movements?"

What would you use a light butt for?

"Isn't this all a blessing from the Apostolic Union? Ah, Lord Yeonju must know this too."

This clueless kid.

Why are you spreading rumors all over the neighborhood that there's a magician here?

The lords' eyebrows twitch.

"Thank you for your kind words, but aren't we here to discuss something more important?"

What? Are you trying to fight now? Are you sure?

"Ahem."

"Okay, if our Gwangryongseong receives an official apology from Choryubukducheon, we will cover up this matter."

Gwangryongseong did not have a lord or successor.

That means the damage was minimal.

In addition, if it's agreed that the disciples died while searching for the treasure, it's not a situation where the elder should be blamed for this damage.

But the super-fast Bukducheon was absurd.

Why are they demanding an apology from us after they attacked us first?

Shouldn't there be a case where the victim apologizes to the perpetrator?

Of course, Choryubukducheon never apologized even when he was the perpetrator.

Not only was it absurd, it's also infuriating.

The Supreme Elder of the First Heavenly Boldutcheon selects the Great Sword.

"Even the enemy was too much! You earthworms dared to harm the Little Heavenly Lord of the Big Dipper with your vile attack!"

"Ha! What are you talking about! Why would we harm someone else's successor?"

"Even if you try to avoid it, it's no use! Now, look carefully! This was the proof of your trickery, protected by the death of our disciple of the Big Dipper!"

The Supreme Elder of the First Heavenly Boldutcheon throws the water bottle away.

The Great Elder of Gwangryongseong picks up the water drop that fell on his feet and examines the pattern.

"My Five Heavenly Dragons, Opilson? Why do you have this card? Opilson was killed in the attack of the Hyeon-ga Mountains and Rivers! Oh yeah, you bastards joined forces with the Hyeon-ga bastards to attack us!"

"What are you talking about! Why was Boncheon attacking Gwangryongseong!?"

"Are you planning to evade your duty? I clearly saw with my own eyes those men in the uniforms of the Hyeon-ga Mountains and Rivers committing a senseless massacre!"

"No, I told you we didn't do that!"

The elder of Hyeon-ga Mountain and River beats his chest violently.

"We also lost our lord to the attack of the Suwangseong bastards. While we were busy recovering his body, which they had torn to pieces, how could we—"

"Go! Weren't you the ones who attacked first? You're the ones who lost the successor, and then blamed it on us!"

In this chain of hatred, everyone shouts and draws their weapons.

There was an air of imminent bloodshed, as if a knife fight would break out at any moment.

Everyone thinks, isn't something strange?

"Wait, wait, isn't this situation strange and coincidental? Let's sort it out. So, they attacked Suwangseong first in Hyeon-ga Mountain and-"

"I told you we didn't do that!"

"No, let's just say I did it and listen-"

"I didn't do it, but you're saying I did it!"

"Fuck, then let's change it to claim, claim. The current status was that the King of Waters was attacked by the Hyeon-ga Mountain Stream first."

The eyebrows of the guardian deity of the water king twitch at him.

But for now, let's hear more.

"And isn't it true that Hyeon-ga-san-cheon was attacked by Gwang-ryong-seong, Gwang-ryong-seong was attacked by Cho-ryu-buk-du-cheon, Cho-ryu-buk-du-cheon was attacked by Bon-geom-cheon, Bon-geom-cheon was attacked by Jeol-nak-seong, and Jeol-nak-seong was attacked by Gang-pae-cheon?"

That's when the representatives' gaze turns to Elder Kang Pae-cheon.

"We were attacked by the Blood Cult."

"Blood sect!" "Blood sect!" "Blood sect!"

As if something had happened, a bloody sound suddenly came out.

"A blood cult? Are you sure? Do you have any proof?"

"Didn't those Blood Cult kids even leave behind a bloody letter, claiming it was their doing! And how magnificent was that handwriting? Why would they be using it for Blood Cult business? It was such a magnificent handwriting that, if sold alone, they could make a living for generations. The strokes were thick and straight, unwavering, and it was clearly a masterful, systematic brushwork that had mastered the Eight Dharmas! And that wasn't all? The spirit within it truly contained images that would shake the world…"

"Hmm?"

Everyone in the audience tilted their heads at the sudden praise for handwriting.

"No, what? Then, let's take a look at the blood sect's writing."

"Ah. That. It's written in blood on the wall. If only it had been left on the corpse…"

The six elders muttered with regret.

Well, wasn't the wind and rain blowing like that?

There can be no writing left in blood on the wall.

The Sapa executives in the group exchange glances.

Isn't that kid feeling sad right now?

No, what if you left it on the body? You were going to take it off, stuff it, and hang it up?

You say that your master died and his disciples were massacred? But do you regret that the writing was erased?

I've heard rumors that he's obsessed with handwriting. But there's a limit.

Still, judging by that little rascal, he doesn't seem to have made up a lie. A fool like that wouldn't be so clever as to pretend to regret a note that wasn't there.

He was an elder who unintentionally bought faith.

And he succeeded in leaving a big question mark on the leaders of Sapa's magic exploration team.

By the way, what's so great about this handwriting?

And I'm curious too.

How great must the writing be that you're ditching the story of the Blood Cult for the writing?
