\chapter{Journey to Changbai Mountain (2)}

In the beginning, a Buddha existed, and the moment that Buddha opened their eyes, three thousand worlds came into being.

Thus, this Buddha was called the Primeval Buddha, meaning the origin of all things.

The Primeval Buddha was also known by other names, Vairocana Buddha or Mahavairocana, all of which mean Dari (大日), or 'Great Sun'.

What distinguished Mahavairocana from other Buddhas was that Mahavairocana was never born (無生).

This was because he existed from the very beginning.

Since no one gave birth to him, he naturally could not have been born.

And furthermore, he conceived and created all things in heaven and on earth, thus being the mother of all, the most ancient mother (老母).

Therefore, some who follow this great fire and pursue its brightness call Mahavairocana by another name.

Wusheng Laomu (無生老母)!

Meanwhile, the current world was flawed.

The good should receive blessings, and the wicked should be punished, but what was the world truly like?

The good, in their benevolence, were ruined and cast onto the streets, dying, while the wicked, through their evil deeds, flourish and succeed.

Thus, the status of the wicked rises, and the status of the good declines, and the world increasingly becomes a harsh hell.

However.

Darkness was destined to vanish before light.

Someday, when the promised time arrives, the greatest demon will descend from the heavens and shatter this corrupted world.

And at that time, only the good will survive, for Wusheng Laomu will lead all good people to that true world in the heavens.

At one time, the good dared to prematurely judge this great will with human thoughts and made a grave mistake.

It was the mistake of trying to welcome Wusheng Laomu by helping the greatest demon, who had descended upon the world, shatter it.

However, it was *we* who were shattered.

The false destruction that Wusheng Laomu spoke of was, on the contrary, the hatred that good people harbored, bleeding from being wounded by the harsh world.

Thus, the good people who cast aside hatred, those who followed the great fire and the light, unbound the shackles of hatred that they had placed upon themselves and finally enjoyed peace in a truly bright world.

That's right. God existed.

God exists. And she was a Zhongyuan person.

But alas,

This truth could not be widely revealed.

The world was still immoral and full of wicked people who slander this true God.

Therefore, until the day the good people cover the world and finally reach the great cause, this secret must be hidden from all but the truly faithful.

Furthermore, she herself did not know her true identity.

However, light exists not to be revealed, but to shine brightly where it exists.

"Great Young Lady, would you like some fish jerky here? Fishing went quite well last autumn, and when I dried it roughly, it tasted really good."

"Oh, really? Let me try, *munch munch*. Oh, this is delicious! What is it? It tastes like the best thing I've eaten!"

"Hehehe, you flatter me."

"No, I'm not just saying that, it's genuinely delicious! You could sell this. No, you should sell this for money."

"No, it's just something I made roughly that happened to turn out well. Who can guarantee it will turn out well next time?"

"Ah, is that so? That's true too."

For reference, that 'roughly' was like this:

Carefully cleaning only large fish with thick flesh and lots of oil, meticulously removing countless small bones characteristic of freshwater fish one by one with tweezers, drying them when the sunlight was good, alternately smoking them with applewood and lacquerwood, and putting them out and bringing them in for four months to create the jerky, which was then torn into bite-sized pieces by hand.

If he were to do it 'roughly' twice, it would kill a person.

But how can one explain that there was the presence of an incarnated deity in the human world, and that you could see her directly, and even offered tributes directly to her?

It was truly a wonderful thing, but there was no way to describe it!

Now, the preparation of tributes by the cult followers has entered a new realm.

What good would it do to offer ordinary snacks!

More special tributes must be offered!

But it's not like they can just buy anything and offer it, so the answer was handmade, homemade snacks!

Thus, when the divine person visited, they would subtly offer the tributes made with utmost sincerity.

Of course, it was a passion for pure self-satisfaction, so if anything, it was closer to a productive hobby activity that they were deeply engrossed in.

"Oh, Young Lady, have you arrived? You're going far again this time, aren't you? I tried making xiangchang for the first time, and it seems to have turned out quite well. You can eat it when you're bored, or slice it thickly and add it when you boil soup."

"Oh, xiangchang. But can I accept it? Didn't you make it to sell?"

Xiangchang (香腸) was a food made by stuffing ground meat into animal intestines and drying it.

It's not difficult to make, but it's hard to dry, so many spoil or rot. Among those, delicious *seokjang* was considered a top-grade ingredient.

"It's not good enough to sell. I wasn't sure if it turned out well, so if you eat it and tell me what you think, I might consider a career change. Haha."

"Then, where. Hmm."

Qing munched and then swallowed.

"This is no joke, you seriously should change careers! It's not salty, and wow, how did you dry the fat so perfectly firm?"

"Hehe, thank you. Ah, but is there anything else I could add to the flavor? There's no big reason, but if I'm preparing for a career change, shouldn't I try making various flavors?"

"Hmm, making it spicy would be good too. Completely spicy, well, only people who like spicy things would like it, so it might be a bit ambiguous."

At that, the Xue Family's Trading Company employee's eyes sparkled.

"Indeed, spicy. Understood."

In addition, a flood of handshake requests and sleeve-stuffing gifts poured in.

"I've recently found joy in baking cookies, please try some Goryeo cookies."

"Dried lamb…"

"It might snow heavily, so take a pair of snowshoes with you."

"I picked this up on the way, do you need a huoshezi (fire starter)? I tried to find the owner, but no one came forward, and I don't have any use for it anyway…"

"The peanut harvest was good, so some beef jerky…"

\textit{Hmm, who carelessly drops such an expensive huoshezi\footnote{火攝子} around, and what does a good peanut harvest have to do with beef jerky?}

Anyway, there was a kind of passion, or perhaps momentum, that said, 'Please, just accept it'.

Thanks to this, when Qing entered the Xue Family's Trading Company, she was already clutching countless pouches in both hands.

Cui Liwen looked at the scene and offered a faint smile.

He already knew that everyone had been racking their brains and concentrating on making the contents of those pouches, so wasn't all of that respect and love combined, what they called reverence?

"Granmps, I'm here."

"Why did you come down so quickly? And Ciyu? Did you leave her somewhere and come alone?"

"The road is long, so I plan to go and come back quickly. I'm thinking of hurrying this time. Where's Yi-mei?"

"What? Going somewhere again? Besides, why didn't you tell me in advance so I could prepare?"

"What's there to prepare? Just taking money and myself was enough. So, Yi-mei is-"

It was at that moment.

Suddenly, a shadow fell.

Qing looked up to see a black object obscuring the sun.

Soon, the sun shone brighly again.

And the black shadow rapidly approached, taking on a human form.

\textit{What is it? Flying Yi-mei? Why is she flying?}

And *thud*!

It wasn't flying, it was a fall.

*Thump!* With a loud crash and a slight tremor, Jian Buxi slammed into the frozen ground, which was hard due to winter.

"Yi-mei!"

Qing rushed to the fallen Jian Buxi.

"Oh, it's Xiao-mei. Hehehe…"

Jian Buxi gave her characteristic innocent yet lewdly alluring smile.

However, even as she smiled, drops of blood trickled down from her forehead, pooled in her eye, and then flowed out as bloody tears.

"Yi-mei?"

Jian Buxi raised a trembling hand to Qing's cheek, then it dropped limply.

Gasp! Jian Buxi is dead!

At that, Qing's heart sank.

\textit{I need to get out of here, right now-}

"Hmm? Who is this?"

\textit{Damn, too late.}

At the voice that followed, Qing's expression soured completely.

It was utterly rotten.

"Ugh."

"Why that expression? What, you're not complaining that the training being a bit rough, are you? A drop of sweat now replaces a drop of blood later, so you have to get beaten and pass out and all that-"

"No, of course that's natural. Isn't that how training is supposed to be?"

"Hmm…?"

Qing nodded.

Even for Qing, training with her Master always ended with her passing out, and sometimes it didn't even end with passing out.

Train as if it's real.

If it were real, she'd be dead, but since it's training, it just ends with some pain, injuries, and passing out.

At that, a fleeting expression akin to pity crossed the man's face.

A handsome man with thick features, masculine.

In this winter, with his upper body completely bare, each of his toned muscles revealed its presence, making him an excellent anatomical model that showed muscle locations without needing dissection.

A peculiar feature was an eye patch diagonally crossing his face. The one-eyed man looked at Qing and grinned, somehow exuding wildness yet brimming with a welcoming smile.

"When you finally see your son's face, you should at least welcome him with a bright smile. Don't you think?"

"Mom". The one-eyed man added.

"Kyaaaak! I told you not to do that!"

Qing cringed terribly.

\textit{Come to think of it, I forgot about this bastard.}

This bastard, Qing's adopted son and Ciyu's older brother, was the former Heavenly Supreme, and now a man whose true identity was unknown, Yan Huining, let out a satisfied chuckle.

Incidentally, this astonishing adoption was not by Qing's free will, how could she refuse when he was threatening her with a sword, telling her to be his 'Mom'?

Whether its Profound Realm or Demonic Ascent, a super-duper master  has the privilege of choosing his 'Mom'.

"What, you're leaving again? Mother, you must have wanderlust. But it's really upsetting, you know? You cherish my younger sister so much, yet you discriminate like this when both of us were children born from another's womb?"

"Perhaps it's the difference between a daughter and a son…"

"Is that so? Then I can't help it. It's a bit unsightly for an older brother to be jealous of his younger sister, oh, right. That actually makes sense."

"What? What do you mean?"

"If I didn't have a younger sister, I probably wouldn't have just quietly put up with this unfair treatment. When you say 'younger sister,' it makes me want to protect her, you know? What's with your expression, Mother?"

"I was just thinking that you really never had a younger sister."

\textit{If he had a younger sister, he would never have said such nonsense.}

\textit{Hmm, come to think of it, I wonder if that pig-headed girl in my hometown was taking good care of Mom and Dad.}

\textit{If she could just catch some dim-witted, dull fellow and give them a grandchild or something.}

Qing tried to erase the thought that came to mind.

\textit{Well, what's the point of thinking about it now?}

Qing looked down at the slumped Jian Buxi.

\textit{Opportunities to receive proper instruction a true master like Yan Huining that give a thourough lesson could make you faint are rare. It feels a bit awkward to ask her to come along just for my convenience.}

\textit{If Yi-mei were there, I'd get countless benefits like automatic change of clothes and automatic bathing, and most importantly, I could gain psychological stability from patting her.}

\textit{But isn't it more important for Yi-mei to escape the lower ranks quickly?}

\textit{Only being at the peak of Transcendence, how can a martial artist live with their head held high with such a realm?}

\textit{Ugh, it's terrible. If it were me, I'd throw away my sword and go farming immediately. The peak of Transcendence, how can a person be like that?}

\textit{So, for Yi-mei's sake, well, it can't be helped…}

\textit{This time, I'll go and come back quickly.}

\textit{Well, when have I not traveled alone?}