\chapter{Journey to Changbai Mountain (1)}

Things to do before departing for Changbai Mountain.

First, bid farewell to friends.

"Farewell, Zhuge."

"Yes, Sister. Please take care. I'll see you later in our section of the Wulin Alliance."

Anyone from the Wulin Alliance might retorted, 'Since when did Wutian Pavilion, the highest-ranking guest hall of the Martial Alliance, become your Half-Sword Double-Saber faction's territory?'

On the other hand, listening to Zhuge Lixian, a giant muscular man six and a half feet tall, bend at the waist, really gave off the impression of a local gang member from her hometown.

"Please send my regards to Xiang'er too. Wow, it's been so long since I've seen Xiang'er, how long has it been?"

"It's been a little over half a year, Sister."

"It's already been over half a year? Wow, time flies."

"Please visit sometime later. Xiang'er must miss you very much too."

Zhuge Lixian returned!

\textit{I did consider taking him along on the way to Changbai, but the Zhuge Family is close, and going from here by boat would make it a comfortable one-day trip.}

\textit{Since it only takes a day to go home, there's no reason to wait and go together.}

\textit{Of course, even without that, there's no reason to hold him back and make him wait just because he's going home.}

\textit{If we part this time, we'll see each other next time.}

\textit{Farewells should be simple.}

In that sense, Peng Daesan was also a farewell.

"Are you going too, San? Please send my regards to Chaolei. Ah, I said I'd visit once, but I still haven't been able to."

"There's nothing much to see if you come anyway. And even if you do come, I won't be in the Clan anyway."

"Funny. Who said I am going to see San? I'm going to see Chaolei."

"Hmph."

Peng Daesan snorted.

Then, after briefly looking at Qing.

"…You're not really planning to come, are you?"

"Hmm, I don't know yet. I might drop by for a bit on the way back from Changbai Mountain? Isn't it right in between?"

"You're going to Changbai Mountain? That's not a place for sightseeing."

"I'm looking for something."

"Hmm. If you must go, it would be better to leave as soon as possible. You should depart in early spring so it will be summer when you arrive."

"I'm planning to go right after I put down my luggage anyway."

"Hmm."

"Anyway, San, take care too."

\textit{So, those who are going home, went home.}

\textit{But Gunyeong as standing next to me as if she's naturally coming to our house?}

\textit{Of course, Gunyeong has nowhere to go after being kicked out of the Ice Palace, but doesn't she have her own room in the Wulin Alliance?}

Well, anyway.

Things to do before departing for Changbai Mountain.

The second.

Listen to the lovesickness and devotion of Siliang and Lianshu, who were on duty at the main gate today.

First, Siliang.

"Oh, Great Junior Master, you're here! Great Junior Master, Great Junior Master, do you know? They say if you see someone too beautiful, the shock can make you lose your memory."

Siliang said.

"Oh, Great Junior Master, you're here! Great Junior Master, Great Junior Master, do you know? They say if you see someone too beautiful, the shock can make you lose your memory."

Siliang blinked and said again.

"Oh, Great Junior Master? When did you arrive? I heard before that if you see someone too beautiful, the shock can make you lose your memory."

Siliang tilted her head and said.

"Oh? Great Junior Master? Are you going out? Ah, Great Junior Master, be careful. If someone sees someone too beautiful, they might lose their memory – Ugh. They might loshe their memowy."

Siliang continued her flattery even with a candy suddenly popping into her mouth.

"Woah, woah, calm down. Lianshu, have you been well?"

"How could I be well? Great Junior Master wasn't at the mountain gate, and Ciyu wasn't here. No, Ciyu! For Ciyu, my life, my light, my salt, my candy, I think I could even give up tonight's snack! Hehehe, Ciyu, *sniff*, Ciyu's smell, hehehe…"

Ciyu looked up at Qing with a crooked neck, leaving Lianshu burying his nose in her nape.

Her expression was like, 'This person is strange'.

"Alright, alright, good work."

"Yes, Great Junior Master!"

"See you later! But ah! Oh, right, did you hear? I heard it the other day, but they say if you see someone too beautiful, the shock can make you lose your memory. It's true."

\textit{No, did she take this opportunity to go overboard once more?}

Qing smiled with her eyes and pointed at Sarang with her finger, saying "Ooh."

At the tip of her finger, Sarang somehow puffed out her chest triumphantly.

To Changbai Mountain (omitted) The third

Meeting and greeting the Sect Leader.

"Oh, Youngest Sister, you're back safely? Oh my, what's all this? Alright, I'll keep this and eat it all by myself."

The Sect Leader, Wang Juhee, who received the dried shiitake mushrooms, immediately put them into her office drawer.

While shiitake mushrooms might be common in Qing's homeland, they were originally the 'king of mushrooms,' capable of making even pine mushrooms or truffles seemed like mere trifles, truly the strongest in the mushroom kingdom.

Of course, if they were truly rare, the Sect Leader would not have said she'd eat them all by herself.

In fact, the Xue Family's Trading Company genuinely offered food ingredients from all over Zhongyuan to its owner's family, which was why she said she'd eat them alone.

"Still, you should have spent the New Year's in the main sect. Right, you said Yunnan. Nothing special happened, did it?"

"Something special did happen, so…"

Qing poured out her characteristic rambling story.

Although the sequence was somewhat jumbled, a Sect Leader of her caliber would surely possess the ability to miraculously understand even a disorganized report.

"The world is truly chaotic. It's truly worrisome that those scoundrels from the Blood Cult keep appearing. Should I send a message to Master? We must be even more careful at times like these."

The location of the Divine Maiden Sect was actually not very good, as south of it was closer to the territory of the unorthodox sects.

Still, it's fortunate that Wudang and the Zhuge Family were nearby.

It's even more fortunate that Qing annihilated the Lulin's main stronghold.

"Alright then, get some good rest."

"Actually, I think I'll have to go out again soon."

"Oh, right after you arrived? This girl, why don't you stay home? Where are you going this time?"

"To Changbai Mountain…"

"Changbai Mountain? Oh dear, it will take at least half a year to go and come back. Hmm."

Wang Juhee's expression somehow became benevolent.

"Although our Youngest didn't raise a thief in the Divine Maiden Sect, no disciple of our sect considers our Youngest an outer disciple."

"It's not like that. This is my home. It just feels like I need to be busy moving around right now."

Wang Juhee was asking if Qing felt uncomfortable in the Divine Maiden Sect because she was an outer disciple.

Qing was not a disciple of the Divine Maiden Sect but always a disciple of Ximen Surin.

She was told not to feel uncomfortable in her Master's sect, especially when her Master wasn't present.

Qing replied that it wasn't like that, and a smile returned to Wang Juhee's benevolent expression.

"At your age, having achieved harmony, it would be fine to rest enough, but then again, that's probably why our Youngest reached such a realm. Still, don't make us worry too much."

"Yes, I'll keep that in mind."

Changbai Mountain blah blah blah, fourth.

Playing with Chen Changming.

"What? Going out again?"

Chen Changming, with herchin resting squarely on Ciyu's head, puffed out her cheeks.

\textit{No, who is this grown-up trying to act cute?}

\textit{Of course, Chen Changming looks like a sixteen-year-old kid on the outside, but how old is she this year? If she's two years younger than my public age, then she's twenty-one, isn't she?}

\textit{Puffing out her cheeks at twenty-one years old… well, it doesn't matter, but I wonder if it's not a bit shameful for herself.}

"Who are you trying to be cute for?"

"Hmph. My business."

"What's the point of playing? Work your butt off when you're young and retire early. Once I reach the Profound Realm, everyone's left behind. You won't see me step a foot outside the house."

"Is Profound Realm some dog's name?"

"For a true master, it's a dog's name. Oh dear, our Changming is destined to train her whole life. Let's retire when we die. Tsk tsk."

A vein popped in Chen Changming's forehead.

"Hmm, in that sense, why don't you teach Ciyu the Thousand Character Classic? Changbai Mountain is too far, and I heard it's dangerous."

"Heeng. Me too."

At that, Ciyu acted cute.

But since Ciyu was inherently cute, it could be said that she isn't acting.

Liaoning Province was clearly Zhongyuan territory.

However, beyond that, Jilin and Heilongjiang were somewhat ambiguous, and opinions were divided.

From the Imperial Court's perspective, while officials weren't officially dispatched, a large number of Zhongyuan people lived there, so it was implicitly recognized as Zhongyuan territory.

Of course, the Jurchen barbarians there would never agree to this.

Originally, Jilin and Heilongjiang were the provinces where the past Jurchen barbarian Jin Dynasty was located, and now the Great Jin was split into hundreds of tribes.

There, each tribe occupied its own territory and claimed it as its own land.

In addition to the Jurchen people, Mongolian barbarian tribes have also subtly infiltrated and were claiming their territories.

There were no Zhongyuan officials, and the tribal laws vary greatly depending on the tribe, with Jurchen and Mongolians in disarray.

So, if you had to say, it's everyone's land, but at the same time, no one's land.

In other words, it's a chaotic lawless land.

However, in the large and small cities along the main roads, the laws of Zhongyuan generally apply and order was maintained.

To be precise, only the single road connecting Liaoning to Harbin, or from Zhongyuan to Heilongjiang Province, was Zhongyuan territory, and the rest was, in Qing's homeland's terms, a joint management area.

As a result.

"Not this time. They say you'll encounter bandits and mountain brigands, those robbers, taking turns being Mongolian, Jurchen, or Dongyi\footnote{Korean and Japanese} barbarians, a total of six times a day. It's too dangerous for Ciyu."

"Heeing…"

Ciyu looked glum.

\textit{But what can be done? It's a land teeming with robbers, a land where 'heh heh, all robbers are dead, people who should be killed are overflowing.' It's truly a land flowing with milk and honey. It's no wonder Grandfather Tangun\footnote{the mythical founder of Gojeoson, the first kingdom in Korean peninsula} settled there.}

\textit{Did Tangun Halabeoji also enjoy punishing villains?}

"What? Why are you so happy?"

"Ahem, happy? It's just that I think about not being able to go with Ciyu and our Changming, and oh, my heart. It hurts so much, really. It's so regrettable."

"Daughter, your Dad is already a lost cause. Let's just us live happily."

"What about studying?"

"No studying."

At that, Ciyu turned her back and hugged Chen Changming tightly.

A vein bulged on Qing's forehead.

\textit{These little ones are just messing around.}

\textit{What the heck, alliance of tiny things?}

"Didn't I tell you to finish the Thousand Character Classic? How can you eat when the child is illiterate?"

"Teach it yourself. I can't teach. Right, Daughter?"

"Yeah. Yeah. Right."

\textit{Well, I suddenly left Ciyu in her care right after arriving, so it must be her way of expressing dissatisfaction.}

\textit{Well, it can't be helped.}

\textit{Studying can be done later, anyway. Ciyu isn't going to be a government official, so what if she's illiterate?}

\textit{Our little Ciyu, just be healthy for me. She's still cute, so it's fine.}

\textit{When she's not cute anymore, then she can study hard.}

Still, after spending the New Year outside and coming back, staying only one night felt a bit awkward.

So, she decided to stay two nights.

"Great Junior Master! Have a safe trip!"

"Oh, you're leaving again, Great Junior Master. I'll guard the main gate forever until you return."

"Hmm. You're not the only ones on duty, are you?"

"Junior Master, I'm not asking for anything, but I heard the bracken is really good in Changbai."

"Bracken accepted."

"Come back quickly. Ciyu will wait."

"You must listen to your Mother, okay? Study hard."

Ciyu subtly averted her gaze.

Qing looked up at Chen Changming, who shrugged her shoulders. 

\textit{Hmm, she's not really just going to play, is she?}

"I'll be waiting, Young Lady Ximen."

"Yes, you're training so hard, but I wonder why you're over there."

Xue Iri was naturally among those seeing them off from the Divine Maiden Sect.

Xue Iri remained.

Qing refused Xue Iri when she offered to go with her.

Well, how could she go with her for something so 'honorable'?

Since it's a journey to find Demonic Arts, and one of the Ten Great Demonic Arts of the world at that, it's better not to get involved, even if they're friends.

Leaving behind the Divine Maiden Sect and a few others seeing them off.

Departing for Changbai Mountain.