\chapter{But It Wasn't Like That (3)}

In the distant past, when the Heavenly Slaughtering Star appeared, every child born under its light was sought out and killed.

Still, this was not enough because of selfish mothers who hid the births of their own children. As such, everyone born within a generous hundred days before and after was also killed without exception.

Much blood and tears had soaked the earth.

However, a child born under the ominous, solitary star of Heavenly Slaughter had to be eliminated, even at such a cost.

Otherwise, instead of merely soaking the earth, a massive wave would come, submerging the land under a sea of blood and tears.

Heavenly Slaughter was a madness humans could not dare to endure.

And it was a madness that grew as one aged.

At first, it was limited to finding the sight of blood aromatic, as well as enjoying the tearing of flesh and the crushing of bones.

But as the Killing Star soaked deeper into the marrow, one would start to find other forms of pleasure on top of the ecstasy of massacre.
They would laugh at the sight of people's sorrow and despair, realizing there was nothing more thrilling than the pain of others.

And just as so, Qing's gaze was captivated by death.

It was when she was looking down blankly at a living thing writhing at her feet.

Suddenly, Qing's arm moved.

The brilliant sensation of a hard, tightly packed mass pushing against her blade. His muscles are pretty tough, huh? He trained well.

Qing's head turned a beat later, twisting bizarrely to face the enemy.

And there stood a man holding onto his severed forearm.

"Nice to meet you. Have we met before? Or is it our first encounter?"

The Sword of the Yue Maiden fluttered, filling the space.

Originally, the Yue Maiden Sword was a bright and cheerful sword style, but the Imagery intoxicated by Heavenly Slaughter painted a completely different picture.

At this moment, her sword was alluring and insidious.

Like a mosquito sticking onto one's body, it stung the moment it touched, eating away at the flush and clumsily, heavily taking flight.

The tip of the Moonlight Sword pierced and flicked at a tendon. A taut sinew snapped and curled into the muscle. 

With the tendons of his limbs severed, the enemy fell, each of his arms and legs twisting in inhuman directions.

Impressed by the familiar pose, Qing exclaimed in admiration.

"Ooh! An Identity No One Expected\footnote{┏(ºдº)┛}? You know your shit, huh."

Qing stabbed the enemy's side once more before moving forward. The foe's stomach, cleanly sliced through the spleen, swelled up as blood began to trickle out.

This was the present left by Wang Sonman.

Now, Qing had almost memorized the entire insides of a human body.

She learned where to stab and how to dig through, thus knowing exactly what to cut.

Qing ran a finger along the sword blade to wipe off the blood and then smeared it on her tongue.

{\itshape  I'm telling you, this salty and fishy taste is strangely addictive.

  Well then, I should also enjoy the banquet now to-}

"Junior Brother!"

A desperate cry. Qing's head snapped around.

The sight of an enemy holding a sword high above a fallen Daijing Sect disciple. At that moment, life and color returned to Qing's eyes.

Just as the enemy was about to bring down his sword, he stumbled, losing his balance, and fell.

As the Daijing Sect disciple pushed away the corpse in horror, he saw a decoration protruding from the enemy's temple.

It was a binyeo, a hair ornament used to fix a woman's hair in place.

"Are you alright?"

Long fingers akin to white jade pulled out the decoration of the binyeo, accompanied with a voice that was far too pretty to belong in a battlefield.

The Daijing Sect disciple looked up at his savior in a daze.

'My goodness. She is so beautiful.'

The Daijing Sect disciple was spellbound.

"What's going on? Is he not alright? Was I a bit too late?"

After wiping the binyeo on her trousers, Qing reinserted it into her tied-up hair and asked.

The Daijing Sect disciple snapped back to reality.

"Ah. Thank, thank you!"

"Young Lady, thank you!"

A different Daijing Sect disciple, who had been calling out for his Junior Brother, also joined in with overwhelming gratitude.

Qing just waved it off, feeling embarrassed.

"Don't mention it. Fight carefully. Don't get hurt in vain."

The Divine Maiden Sect's Esoteric Doctrine. Form of Hair, Number Eleven.

Twisting the hair largely and inserting seven binyeos.

It was a secret technique of the Divine Maiden where two long binyeos made of steel and five small binyeos that could be used as projectiles were equipped in the hair.

They had said that even in places where weapons were not allowed, no one would ever question a woman's binyeo.

Although there was a drawback of her head becoming exceedingly heavier, the muscles and bones of a Master's neck would never yield to such things.

And with Qing's monstrous strength, even if her hair was densely packed with needles like a pincushion, she would still be able to endure.

Instead though, it would look quite suspicious.

\textit{Hm. For some reason, my excitement is dying down.}

Qing licked her lips as she surveyed the battlefield.

A spirited half-sword strike from Peng Daesan was seen.

His guandao entered the neck and emerged under the opposite rib.

A diagonally torn torso fell backwards with a thump.

{\itshape Ehh? Wot? Why is it so messy? What the hell is that even supposed to be?

  I guess it's to be expected from the immaturity of a Middle Stage nobody.}

Qing darted through the gaps of Daijing Sect disciples, scattering her sword around.

Third Movement of the Divine Maiden Sword, Butch Heavenly Maiden.

The blade wrapped with Sword Threads carved the same trajectory as Peng Daesan, passing through the enemy's body.

However, the outcome was different.

The severed torso slid perfectly along the diagonal cut, spewing out its contents.

{\itshape That's right. This is the true taste of a diagonal slice.

  Sanie is still far from mastering it.

  Or maybe it's a limitation of a half-swordsman?}

Qing nodded in satisfaction.

She held such a cruel yet wondrous aura.

As such, the Advance Blue Brigade hesitated and stepped back while the warriors of the Daijing Sect raised their morale with shouts.

Qing raised her hand in response and surveyed the battlefield.    

There, she saw Nan'gong Shencai.

True to his title as the Sword Lunatic, he was swinging only his sword in solemn silence.

His left hand, its digits stretched out in the stance of a Finger Sword, did absolutely nothing.

{\itshape If he's gonna do that, why not wield the sword with two hands or at least carry a shield?

  Oh well.

  He says that's how he likes it. Who am I to say anything? Anyway.}

And then, she also saw Changbin.

Qing almost flinched in surprise.

\textit{What the fuck? Why does he fight so well?}

The trajectory drawn by Sword Qi broke apart and scattered.

Then, the afterimages of shattered Sword Qi fluttered white and red.

It was no different from a splendid display of blossoming flowers, seeming as if the entire world was filled with scattered petals blown by the wind.

However, it's beauty was not all there was to it.

After all, a wrathful maelstrom that stirred and surged due to the sword carried the petals on the wind.

When the fallen corolla touched the enemy, they reached a full bloom in the shade of blood red, thus blossoming once again.

Qing caught sight of the collapsing enemy.

Not a single part of the enemy's body was unmarred; the petals of Sword Qi left wounds as small as fingernails, causing blood to leak from all over and leaving them unable to regain their senses.

Qing felt somewhat wronged.

{\itshape  He does all that and it's not called a Demonic Art? Are you seriously telling me that's supposed to be something else?

  What the hell? Why is the one I use one of the Ten Great Demonic Arts Under Heaven or whatever?

  That's also cruel, you know? So why only me?}

Frankly, Qing's sentiment was not off the mark.

The Sword of Mount Hua was originally cruel.

Mount Hua's Supreme Technique, Life-Taking Linked Three Immortals Sword, was powerful.

But it was also too cruel.

So much so that even the sect disciples of Mount Hua avoided learning it, saying it wasn't a swordsmanship fit for a Daoist Sect.

Therefore, later generations covered the deep malice of the Life-Taking Linked Three Immortals Sword with developed and progressive martial studies.

And then, they added flashy splendor through the form of change and swiftness.

Thus, the famous Plum Blossom Sword was born.  

However, the cruelty hidden behind the splendor did not simply disappear.

After all, it was a full bloom overflowing with Sword Qi and blood. 

And at the sight of this, the Killing Star, suppressed by the gathered gratitude of the Daijing Sect disciples, quietly raised its head once again.

\textit{Right. I can't be pushed back by his performance! I can do more than that!}

Qing plunged into the midst of foes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Yeom Saraedal realized far too late that the situation had gone terribly wrong.

The Advance Blue Brigade was supposed to be a special force of the Demonic Cult, composed of members that were in the First-Rate Realm at the bare minimum.

They should have swept through the remnants of the orthodox fodder in an instant and then crowded around him to watch the spectacle.

Instead, they were being thoroughly cut down.

It was because of the youthful Masters extending out streams of Sword Qi.

They were Peak Realm Masters at the very minimum.

Among them was even a Plum Blossom Swordsman of the Mount Hua Sect.

Yeom Saraedal's stomach was burning in frustration.

What the Second Coming of Yan Liang, Yeom Saraedal, wished to do:

To kill the enemy by slowly draining them of their blood, as they inwardly drowned in the guilt of their subordinates dying because of their own shortcomings, as well as the despair of hearing and seeing the destruction of the organization they had created with their own hands.

What the Second Coming of Yan Liang, Yeom Saraedal, actually faced:

The crisis of losing a combat unit of the Divine Cult due to underestimating the enemy's power.

His stomach burning in frustration and agitation as his subordinates were dying.

Sure, losing beloved subordinates was regrettable, but more importantly, his own safety was paramount.

What fate would a boss who had ruined his unit face?

Obviously, higher-ups of the Divine Cult would not just let it slide.

Yeom Saraedal's expression gradually darkened.

It was the decisive difference between the Orthodox Faction and the Unorthodox Faction. The mindset that the martial artists who walked the White Path possessed compared to the martial artists who walked the Black Path.

It was also the difference between those who looked for an ‘us' in dangerous situations and those who looked for a ‘me'.

Of course, just because they were of the Orthodox Faction didn't mean they were an organization with only kind-hearted people. 

In the end, Yeom Saraedal made a decision.

Swinging his meteor hammer widely, he released a Qi Wave, forcing Wang Gaeyuk and Guardian Ki to distance themselves and dodge.

Then, Yeom Saraedal fumbled in his bosom.

In the time the two from the Daijing Sect heightened their guard, thinking it might be some ace in the hole, Yeom Saraedal took out a pouch and violently threw it on the ground.

The glass bottle inside the pouch broke upon hitting the ground, mixing with the powder inside.

Soon after, a dense smoke began to billow out explosively.

Wang Gaeyuk and Guardian Ki covered their mouths and noses with their sleeves, hastily stepping back.

"It's poison! Everyone, back off!"

In reality, it was unknown as to whether it was truly poison.

However, shouting such upon seeing suspicious smoke was practically a law in Wulin.

The sound of a shrill whistle spread through the smoke.

It was the retreat signal for the Advance Blue brigade.

And with it, the evildoers of the Demonic Cult vanished into the smoke.

It might have been a mere smoke screen instead of poison.

Many thought so, but actually carrying it out with their actions by jumping into the smoke was a different matter entirely.

After all, there could be a one in a million chance that it was mixed with toxic powder.

Therefore, there were only two kinds of people who could dive into the smoke.

The first type were those who definitively knew the smoke contained no toxic substances.

The retreating members of the Advance Blue Brigade were of this kind.

The second type were those for whom it did not matter whether the smoke contained poison.

These included people who had already taken an antidote or had made preparations in advance.

Or those with a rare Constitution that made them immune to poison.