\chapter{But It Wasn't Like That (7)}

Just leaving them to their devices seemed enough for the two to start grabbing each other by the collar.

But Qing couldn't bear to just watch them fuck around, so she spoke up.

"Why are you guys leaving behind a perfectly good weapon and just yapping at each other? I'll let the bastard who wins go, so……."

By the time she said ‘go', the subordinate had already swung his sword.

It seemed the boss hadn't been all that popular.

"Keuk, you……!"

Yeom Saraedal, having been stabbed in the side, coughed up blood.

Normally, stabbing someone in the side would result in death.

Even a Master couldn't avoid this fate.

"The Divine Cult respects the strong. It is survival of the fittest. There is no need to feel too wronged."

The subordinate was saying something unnecessarily cool when all he did was a cowardly surprise attack.

However, he wasn't entirely wrong either.

No one in the Divine Cult would curse at him for this situation.

Weakness was a sin.

The one who survived was the victor.

That was all there was to it.

Yeom Saraedal, who had been stabbed by his subordinate, would be deemed the retard.

And a hearty laugh of ridicule would be the icing on the cake.

After all, that was how the Heavenly Demon Divine Cult was like.

Heavenly Demon Divine Cult!

Its roots lay in a religious group known as the Divine Cult of Sun and Moon.

Originally, Zoroastrianism was adapted over time to suit the tastes of the Chinese, thus becoming the Divine Cult of Sun and Moon.

The Divine Cult of Sun and Moon believed all of Zhongyuan should follow the will of the Sun God, Ahura Mazda, and the Moon God, Angra Mainyu.

They dreamed of religious victory.

And they actually acted on it.

It was an attempt at a kind of reform.

And as history had shown time and time again, rulers never kindly accepted challenges from religious zealots.

The Emperor harshly suppressed the Divine Cult of Sun and Moon.

As a result, the cult fled to the desolate land of Xinjiang, dreaming of revenge and forming a community.

The representative of this community was the greatest Master of their religion, who had led the Divine Cult of Sun and Moon to safety against the government's forces.

He proposed the following upon becoming the Cult Leader.

Ahura Mazda, who was the sky.

Angra Mainyu, who was the devil leading to the world's end.

The sky and devil shall be combined as one to be called the Heavenly Demon.

It was the birth of the Heavenly Demon Divine Cult.

They ground their teeth, forever hoping to someday dye the lands of Zhongyuan with the holy fire of the Divine Cult.

In fact, every once in a while, they would invade Zhongyuan' Wulin.

The First. The Second. The Third, and even the Fourth.

It was the history of four Great Wars Between Orthodox and Demonic.

In Zhongyuan where blood was shed, the Heavenly Demon Divine Cult was derogatorily called the Demonic Cult, thus stripping away all the "good" words in the name.

To the followers and believers, it was the Heavenly Demon Divine Cult; to the people of Zhongyuan, it was the Demonic Cult. Though two names, it represented just one entity.

"Um…… Great Expert?"

The victorious subordinate looked at Qing, trying to gauge what he should do now.

Qing asked.

"What about Bokshinjeok?"

"It is in his possession."

The subordinate pointed at Yeom Saraedal.

The dying Yeom Saraedal glared.

However, what was there to fear from a bastard who was already on death's doorsteps?

"Nice. Then, go."

"Thank you for your mercy."

The subordinate bowed with a fist and palm salute before leaping away.

Qing promptly extended her palm.

"How dare you!"

Ding! Along with the sound of a bell that shook the entire stone chamber, the subordinate's buttocks exploded.

Each of the legs, having lost the butt, drew separate parabolas and only the remaining torso fell pitifully onto the tomb slab.

The subordinate lisped faintly with aggrieved eyes.

"Uweheee, uweheeeee……."

"What do you mean ‘Why'? I said I'd let you go, not that I wouldn't attack, right? You should have dodged it if you wanted to live."

"Fuuuuuuccccc……."

With a look full of resentment, the subordinate breathed his last.

Qing whistled as she rummaged through the corpses.

After all, acquiring spoils was the natural right of the victor.

"Ah. They're broke ass motherfuckers……"

\textit{Would it kill them to carry around a few gold coins?}

The best she found was a caidai that could be strapped to the thigh and throwing knives with flower decorations that were neatly inserted into it.

\textit{Did this dumbass like floral patterns? Even though he looked like some forest bandit?}

Qing strapped the caidai to her thigh and tied it to her belt.

She was quite pleased at how it didn't bother her or feel out of place even when she tried stretching her legs out as far as possible.

It seemed there was no need to grab a handful of chopsticks at every inn anymore.

Finally, ten thousand gold, no, Bokshinjeok was held in Qing's grasp.

Not only was it surprisingly long, but it was also quite heavy, perhaps because it was made out of iron.

She heard it was made of Cold Iron, but she didn't expect it to actually feel so chilly in her solid grip.

There were holes drilled into its long body, so it seemed to be a flute.

However, with no decorations whatsoever, it looked nothing more than a dull, blueish stick at a glance.

\textit{Wow. Imagine hitting someone with this. Wouldn't it feel fucking incredible?}

Whoosh. Whoosh.

Qing swung Bokshinjeok around.

Its weight, length, and handle were perfect.

\textit{Perhaps even that legendary blacksmith or whatever made it as a makeshift club for emergencies?}

If Banchi heard this, he would have wept tears of blood.

Qing, having tucked Bokshinjeok in her waist, surveyed her surroundings.

The burial chambers, lit by the dying light of torches, had become a scene of chaos.

After approaching the stone coffin at the center, Qing gently straightened the faded silk robe covering a withered skeleton and closed the lid.

With that, Qing flew through the hole in the ceiling.

And then…

As the torches burned out, only darkness embraced the burial chambers left in shambles.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Daijing Sect Leader, Wang Gaeyuk, was all smiles.

And why wouldn't he be? He had achieved the greatest feat of his fifty-seven years of life.

Some sect disciples were injured, but there were no severe injuries or casualties.

And they had managed to repel an actual combat unit of the Demonic Cult.

Furthermore, they had also completed the rescue operation for the missing people along the way.

Though, the rescued were but a shadow of their former selves and numbered only about thirty in total.

Since he did not expect for a rescue to be possible in the first place, it was just a pleasant bonus to him.

However, the rescued knew nothing.

They just rambled about how they had been lured by the promise of making it big by Wang Sonman, only to be ordered to dig the earth with shovels upon regaining their senses.

Since the Advance Blue Brigade had either died or fled, the purpose of the Demonic Cult remained unclear.

The only thing known was that they intended to raid the tomb of some unnamed person. That was all.

In essence, the incident was ultimately concluded with Qing securing a trophy worth ten thousand gold.

Truth be told, Qing made no particular effort to conceal it either.

"What is that?"

"Ahhh, Sanie doesn't know, huh. This is called a ‘flute'. You can play it by blowing into it."

"...That is not what I was asking. Can't you carry something a bit more presentable? Why did you pick up something that looks so outright cheap?"

Originally, musical instruments were meant to be ornate.

After all, music was ultimately intended to enchant people.

In the past, music could soothe the hardships of labor or add solemnity to rituals.

And even in the present, it could help one forget the sorrows of love or enhance the taste of liquor.

Therefore, musicians not only endeavored to please the ears but also to delight the eyes, making the ornateness of instruments a natural evolution.

In that sense, Bokshinjeok appeared to be nothing more than a sooty rod.

"I bet even you'll be shocked if you knew how much this was worth, Sanie."

"What, is it worth about two coins?'

"Little Brother Peng, that much would not even amount to the value of its scraps. It should be at least one silver sycee, should it not?"

"Younger Brothers, you are too obsessed with appearances. Such an object could unexpectedly be a trea-"

Changbin's words trailed off, crawling to a halt.

It was because of Qing's piercing gaze, as if he had touched upon something he shouldn't have.

For once, he exercised an insight befitting a disciple of Daoism.

However, Changbin was never treated all that well by Qing in the first place.

As such, Peng Daesan and Nan'gong Shencai simply assumed it was just another day of Qing bullying Changbin into submission.

They simply let his words enter in one ear and out the other, thinking it was nonsensical.

"By the way, Sword Friend. Did you even know how to play the flute?"

Nan'gong Shencai asked, seemingly finding it a surprise.

Had Qing been any other woman, such a remark would have been deemed rude.

After all, playing at least one instrument was considered a lady's virtue.

However, Qing was a man at heart.

Why would she give a flying fuck?

"Flute? What's there to know? I just need to blow into it."

Qing put Bokshinjeok to her lips.

Having seen Ximen Surin play the flute often, the posture she roughly mimicked from her memories looked somewhat passable.

The three of them waited in anticipation, thinking ‘Could it be?' at the sight of her stance.

But sure enough, only a whooshing sound of wind buzzed noisily.

Qing got annoyed and her pride was hurt, so out of spite, she blew even harder into it.

She expected at least some kind of noise, but only a hollow whoosh like the autumn breeze returned.

Qing frowned.

"Agh, shit. Is this thing broken or something?"

San looked at Qing incredulously.

The girl's face had turned red from blowing too hard.

"...Just because you blow into it hard doesn't mean it makes a sound."

"What the, Sanie. You know how to play?"

"Just a simple tune."

"Ooooh, a man who does music. How cool. Then let's hear it. Why don't you play us one song?"

Qing handed over Bokshinjeok.

Peng Daesan reached out to take it, but then recoiled at the shiny marks near the mouthpiece.

"What the. Why? What's wrong?"

"...Please. I am begging you. Don't just flippantly offer items you've put your lips on to others. Especially considering you are a woman. Could you please act a bit more ladylike? Imagine how ridiculous and easy you might look to other men."

Hehhhh? Oh? Now he's even preaching to me?

I already look ridiculous right now, so what does it matter what I do anyway?

Qing scratched her head, then, out of habit, quickly untied and retied her hair.

Her skill at doing her hair was impeccable; she bit the hair tie, quickly rolled, twisted, and wrapped her hair before securing it with a binyeo.

After tying it back as a finishing touch, not a single strand was out of place.

It was the greatest achievement of the nuclear noogie.

"We're friends anyway, so what's the big deal? Mm? Or wait. Maybe it is?"

\textit{Come to think of it, maybe it's a bit grosser since we're friends?}

Qing recalled her school days.

Recorders were something you could never just borrow or lend.

It was kind of gross, after all.

"Sword Friend, why not just play the gu or the qin, then? At the very least, they would make a sound."

"What did you say, you punk?"

Qing stared daggers at her Sword Friend.

But since Nan'gong Shencai was not mocking her but actually offering sincere advice for his Sword Friend's own good, Qing felt even more determined to prove him wrong.

"Just wait and see. I'll get a sound out of this thing if it's the last thing I do. Seriously."

Peng Daesan couldn't help but retort incredulously.

"...Are you truly saying that is all you can achieve? Merely making a sound?"

"Just you watch, okay?"

And so, Qing was accompanied by Bokshinjeok throughout the entire journey to Mount Hua.

No sound ever came out.