\chapter{But It Wasn't Like That (2)}

A temporary shelter made of thick fabric was called a tent.

A man entered such a refuge, pushing aside the entrance cloth.

Boss. The eighty-seventh prospective site is…"

"Oh, Da Bulri. Is it all dug up? Did anything come out?"

The boss, who was lying on a makeshift bed while picking his nose suddenly sat up and asked.

Da Bulri shook his head with an expression full of regret.

The boss exploded in anger.

"Fucking shit! Isn't this jangbodo just a complete sham! We have been digging the ground for eight months, so why! Why is nothing coming out?!"

Jangbodo. A map where treasures were buried, hence, a treasure map.

"Still, by tomorrow, the eighty-eighth, eighty-ninth, and ninetieth prospective sites will be completed. Let's just dig up to a hundred and then return. Who would say anything then?"

"Motherfucker. Damn it."

The boss cursed and flopped back down.

It was then.

"Boss!"

Another subordinate rushed into the tent, panting.

Even while seeing such urgency, the boss remained nonchalant.

"What's the matter?"

"Those Daijing Sect bastards have all swarmed here!"

"What the… That fucker, Wang Sonman. Did he spill everything? Fuck this. This is why you can't trust those Orthodox Faction fuckers. They have no loyalty, you hear me? No loyalty at all."

Then, Da Bulri corrected him.

"Would he have betrayed us after learning the Heart Absorption Art? It must be that he was caught due to some misconduct."

What was the reason for imparting the Heart Abortion Arts and even giving the precious Black Heart?

It was because once exposed, the person in question would become a public enemy of Wulin either way.

Thus, once Wang Sonman took over the Daijing Sect, it was no different from the entire sect switching to their side.

"Same difference. He got caught because he did something wrong? Then it's a betrayal due to a lack of ability. Anyway. Hoo. Hoit."

The boss stood up, bracing himself against the ground, and looked at his subordinate.

"You said the Daijing Sect bastards have come swarming? How many?"

"Around fifty or so? Is what it seems like."

"Fifty, you say. Hm. Da Bulri, what did you say about the Daijing Sect's forces again?"

"There are two at the Early Stage Peak Realm and seven at the First-Rate."

"Ha. Just that?"

The boss licked his lips.

"They're really looking to die, aren't they? Just look at them picking their own graves. Perfect timing. I was starting to get bored anyway. Let's massacre all of them."

"Boss. Our mission is……."

"Agh! Shit."

The boss interrupted Da Bulri.

"I know, alright? But we've been discovered, yeah? So let's wipe them out and escape. What else can we do? Or what? Should we just spread rumors about how we're looking for treasure? No, right? So, what should we do, huh? We did our best. Hm…….. Let's see……."

The boss stroked his chin.

"Just finish up where we were digging for now. We have to at least finish where we started. And prepare to bury all the laborers as well."

"I will follow your orders."

Da Bulri turned around, preparing to leave.

But when he did so, the boss suddenly stopped him.

"Wait. We have to deal with Wang Sonman too. Da Bulri, you take care of it and return separately. If they've all swarmed out, the house must be empty. Assign some other bastard to do the finishing touches." 

"Understood, Boss."

Da Bulri bowed respectively and then disappeared outside the tent.

Then, the boss gave orders to the remaining subordinate.

"Gather all the members of the Advance Blue Brigade. Leave only those finishing the digging. Let's go slice up some people for a change."    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Mount Subyeol was one of the many common mountains in Jianghu.

The terrain was not particularly rugged, nor did it offer stunning scenery.

Since there was a road nearby, there was rarely a reason to traverse it, so apart from the occasional herbalist hiking up with a sack, it was largely untouched by human footsteps.

And according to Wang Sonman's confession, it was also the place where the missing persons had been taken.

It was when the Daijing Sect's rescue team reached the mountain's entrance, at the boundary between the fields and the mountain terrain.

A man stood boldly, blocking the rescue team.

Despite his disheveled hair and greasy, filthy face, his eyes shone ever so brightly, albeit with sinister light.

"Are you the Daijing Sect? I've been waiting for so long, you know?"

The Sect Leader glanced at the Guardian Elder.

After all, it seemed somewhat inappropriate for a Sect Leader to shout with his own mouth.

As such, the Guardian Elder roared with Inner Qi imbued in his voice.

"WHO ARE YOU! REVEAL YOUR IDENTITY!"

"Me?"

The man grinned ferociously.

"This elder's name is Yeomsaraedal." 

"Ahyanliang Yeomsaraedal!"

The Guardian Elder exclaimed in horror.

And as if in response to that, there was a stir among the Daijing Sect's ranks of disciples.

Qing asked Peng Daesan beside her.

"Yeomsaraedal? What kind of name is that? Is Yeom the surname? Or Yeomsa?

"It is Yeom."

"So, his name is Saraedal? Isn't that even stranger? How can someone's name be……."

"It is a name used in Xīzàng\footnote{Tibet}. But……. Never mind. Your ignorance is no longer novel to me."

"If I know, I just need to learn, you know? So, is he a famous person? A strong guy?"

"The Second Coming of Yan Liang\footnote{A general under warlord Yuan Shao from Three Kingdom era}, Yeom Saraedal. Known to be at the Late Stage Peak Realm. No wonder something like this happened. It seems like it was all the work of those Demonic Cult bastards."

The Second Coming of Yan Liang, Yeom Saraedal.

He was a Demonic Adept with a prowess as subtle as his title, said to be the incarnation of Yan Liang.

However, Yeom Saraedal was not famous for his own martial strength.

Rather, he was a Demonic Adept who was renowned as the Boss of the Advance Blue Brigade, a combat unit under the Demonic Cult's External Battle Pavilion.

His alias, the Second Coming of Yan Liang, came from his aggressive assaults, likened to Yan Liang's own.

"The Demonic Cult? Where all those bad guys gather and live together?"

"That's right."

It was then.

The Mission Window, which had been pretending to be absent all this time, finally showed its repulsive form.

\begin{quote}
[Omen, (Unknown)th Crisis]

Description:

[You have encountered a special task force of the Demonic Cult.]
\medskip

Actions for Mission Completion

Righteous Karma) Defeat the Advance Blue Brigade

Evil Karma) Defect to the Demonic Cult and join the Advance Blue Brigade

Heavenly Slaughtering Star) Kill all

[This choice could influence everything below Heaven.]
\end{quote}

This was yet another Omen Mission.

Fucking hell, I've already met the Final Boss, you know? Omen, my fucking ass.

Qing spoke in a grating voice. 

"Ah shit. Hey, San. Even if I chew on poppy now, it'll be a bit late for it to take effect, right?"  

"As I have already said before. The side effects are not to be underestimated, so you should bear with it unless absolutely necessary."

"I'm fine, though……"

Qing liked alcohol.

Though she liked it even before the start of her Wulin journey, it was not to the extent of recklessly guzzling down hard liquor.

But now, she could drink any type of hard liquor as if they were water.

Why? Because she was able to.

To Qing, alcohol was just a beverage that made her feel good.

No matter how much she drank, she maintained a pleasantly tipsy state.

Moreover, since the start of her journey, she had not once experienced a hangover.

Though she was not certain, it was probably due to her choice of Constitution.

Blood Poison.

She benefited from the positive effects of whatever she consumed, while all negative effects were nullified.

The poppy was no different.

She had been sternly warned that over time, the side effects would be as severe as becoming bedridden due to alcohol poisoning, but she had yet to see any signs of it.

To Qing, poppy was merely a drug that made her body and mind feel at ease.

\textit{Strategy Guide, looks like it's you once again. I really hope I can meet you one day.}

Qing sent her thanks to someone who was somewhere in the universe. Or not. Both location and identity was unknown to her, after all.

"But he's at the Late Stage Peak Realm, you said? Then why is he so confident, standing there alone? He acts as if he's in the Transcendent Realm or something."

"He is not alone. Look."

Men in black attire emerged in a line, cutting through the mountain terrain.

"Hey, look here, Daijing Sect Leader. You're just a greenhorn who barely clawed his way to the Peak Realm, yeah? And there's one more, right? Is it that old man clinging next to you? As a special favor, I'll take you both on myself. How about it?"

Wang Gaeyuk and the Guardian Elder looked at each other.

They were friends who had grown old together while raising their sect.

As they were already closer than blood brothers, they understood each other's intentions with just a glance.

'It doesn't look like he knows, does he?'

'It doesn't look like he knows, right?'

Qing and Changbin were at the Late Stage Peak Realm.

Peng Daesan was at the Middle Stage and Namgung Shinjae was at the Early Stage.

"You two old bastards will have to use all your might to defeat me. After all, as time passes by, your frail family members will continue to die."

Wang Gaeyuk and the Guardian Elder exchanged glances with Qing's party and nodded slightly.

Then, with a deliberately solemn expression, they drew their daos and shouted.

"The Guardian and I shall personally confront this evil fiend! The rest of you, annihilate those wicked bastards of the Demonic Cult!"

The implication was that they would handle Yeom Saraedal, so the others should take care of the rest.

"KAHAHAH! That's more like it! Come! Old bastards!"

Yeom Saraedal laughed heartily, oblivious to the situation.

In his mind, the tragic downfall of this Orthodox Faction was already unfolding.

{\itshape Two old men, desperately trying to stop just one of him, while their disciples were dying.

The blood and scream of the orthodox bastards would continue to burst forth, and the old men, at a loss for what to do, would become increasingly engulfed in despair and self-reproach.

And the distorted expressions they would wear at that very moment!

When only the two elderly are left, I will suppress them, mock them, and play with their lives.

I'm gonna thoroughly enjoy their grief-stricken, tragic reactions.}

Of course, everyone has a plan.

However, as Sun Tzu emphasized, know the enemy and know yourself.

This principle was the foundation of all strategies, applicable to all worlds before and after Sun Tzu, and even in those where Sun Tzu never existed.

If you did not know your enemy, you would have to get hit.

After all, ignorance was learned through getting beaten the shit out of. 

"Let's go! We will annihilate the scum of the Demonic Cult and uphold the justice of Zhongyuan!"

As Wang Gaeyuk led the charge with a shout, a chorus of voices followed him.

And thus, the battle began.  

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was having a blast.

\textit{Wow! Legalized slaughter! Free murder! Infinite refills!}

Of course, the law prohibited murder.

But there was the principle of non-interference between the government and Wulin!

Killing among martial artists wasn't just overlooked; in fact, it was even somewhat welcomed.

So, saying it was legalized slaughter wasn't entirely incorrect.

As Qing ran around in ecstasy, she was stopped in her tracks by an enemy.

After all, a girl approaching with light, effortless skips seemed far too easy to handle.

However, the moment they clashed and the girl's sword dug into his blade, he realized something was terribly wrong.

Shortly after, the blade snapped. His left hand's fingers, which he had reflexively stretched out, dropped off one by one starting from the top.

And then, Shwuk. The excruciating pain flooded him.

Qing relished the sensation at the tip of her blade.

It pierced through the soft leather below the diaphragm, tearing through the peritoneum to reach the resilient lining of the stomach.

When she exerted a slight force at that sliver of a moment, the stomach split open and the gastric fluids spilled inside the body cavity.

When the blade was withdrawn, only a cute cut below the diaphragm, a stab wound, remained.

But regardless of outer appearances, she was sure the experience of his insides dissolving in his own stomach acid would be absolutely…electric.

The pain of one's organs melting while still alive was beyond what a person could dare to bear.

The member of the Advance Blue Brigade convulsed on the ground, unable to even let out a scream.

\textit{Teehee, looks like it hurts.}

Qing looked down at her handiwork with an ever so content grin.