\chapter{But It Wasn't Like That (4)}

It was when Yeom Saraedal hurriedly ran away, returning to base.

The youngest three members guarding the excavation site greeted their boss with big, oblivious smiles, unable to read the room.

Yeom Saraedal was about to burst into anger, but paused at what followed.

"Boss! We found it! We actually found it!"

"It appeared right on the ninetieth!"

Yeom Saraedal felt as if he had seen the sun shine through clearing clouds.

This meant the mission was complete!

Even if the Advance Blue Brigade had suffered catastrophic losses, he now had something to report.

After all, the actual Master, himself, had survived and the deputy would return after dealing with Wang Sonman of the Daijing Sect.
That was enough of a result to excuse himself from punishment.

"What about the Bokshinjeok? Did you find the Bokshinjeok?"

"Huh?"

"I asked if you found it."

The youngest members exchanged glances, gauging each other's reactions as if urging someone to speak up first.

Yeom Saraedal spat out curses.

"You didn't even check that? Fucking hell, you stupid motherfuckers."

The juniors felt wronged.

"Where is it? Hurry. Hurry up. Why aren't you running?"

In a hurry, Yeom Saraedal urged them on.

He didn't know when the Daijing Sect bastards might attack.

They would soon realize the smoke screens lacked any poison and could quickly climb the mountain to reach this place.

Of course, Yeom Saraedal knew the way and returned directly.

But the Daijing Sect bastards didn't know the path, so they would probably wander. Still, if unlucky, they could discover this place quickly.

Seeing his urgency, the youngest members quietly led Yeom Saraedal to the tomb raiding site.

The burial chambers of the Heavenly Queen, erected without a mound, was not an easy place to find despite having a treasure map.

Moreover, with trees growing overhead and their roots entangled into the earth, digging was extremely difficult.

In fact, it was to the extent that they had to kidnap people just to have enough hands for digging.

Of course, this was also a decision heavily influenced by the Advance Blue Brigade's reluctance to dig; they considered themselves as one of the great combat units of the Divine Cult. Their members were all First-Rate martial artists at the very minimum. Why should someone like them do menial labor?

A gray stone wall was revealed beneath the excavated ground.

The bricks were clearly man-made.

Yeom Saraedal realized his mistake.

How could an entrance just magically appear directly under the earth they dug-up? It wasn't possible.

This had been a mission that had lasted eight months just to dig and find the underground burial chambers.

In fact, the fact that they found the tomb was a miracle in itself.

Originally, they would have mobilized all workers to dig around to find the entrance.

However, there was no time.

Finding the Bokshinjeok and returning to the Divine Cult was practically his only lifeline.

"Step back."

Yeom Saraedal lifted his meteor hammer. 

If there was no time to dig around, he would just have to break through.

Yeom Saraedal struck down at the stone wall with all his remaining Inner Qi.

Boom! Boom! Boom!

As he was in a position where he was being chased by time, each harsh explosive sound made his heart sink further.

Yeom Saraedal gritted his teeth.

Boom! Boom! Boom! Boom!

How many times did he swing down on the wall?

Finally, the bricks collapsed inward.

And from it, a dark abyss seemed to open its maw.

"Torch."

"Huh?"

"Give me a torch."

"Ah. I will bring it right away."

"YOU MOTHERFUCKER! Shouldn't you have prepared in advance? Didn't you fucking see me breaking the wall?"

Yeom Saraedal rebuked them, unfairly acting as if this was something obvious.

So, the juniors felt aggrieved.

But the law of Wulin was clear; if they were so aggrieved, they should have reached a higher realm and became the boss themselves. But they weren't. And they didn't. So they had no right to be upset about anything.

As one of the juniors hurriedly brought a torch and threw it inside, a burial chamber about one room deep was revealed.

Yeom Saraedal leaped down in a hurry.

Now, if only I quickly find the Bokshinjeok and escape, then…

Yeom Saraedal, who was thinking as such, quickly found his expression hardening.

He had imagined a tomb with a remarkable chest in the center, revealing treasures immediately upon opening it.

However, in the center of the burial chambers, another stone tomb was placed. 

That of itself was not all that bad. To be fair, it was only natural for a burial chamber to have such a stone tomb. 

Rather, the biggest issue was that the burial chambers were surrounded by countless drawers constructed like those of an apothecary's stores of medicine.

As if to say, ‘Try searching if you can'.

"FUCKKKKK…….!"

Yeom Saraedal tore at his poor, innocent hair in fury.    

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing knew the effects of Blood Poison.

Poison nullification. It was a very simple, straight-forward effect.

She couldn't remember the title of the game now. To be fair, her playtime was actually 0 hours. But one of the few things she remembered was that apparently, the enemies in this game used poison quite often.

And according to the posts she read, that made the game even more enjoyable to play.

But why should that matter to her? Regardless of whether it was a trip to primitive, ancient China, a world within the game, or a transmigration to some mirror dimension, her present life had become indistinguishably real to her.

So, when she tried to actually test out her Constitution, she realized that the supposedly simple effect of poison immunity was not so simple after all.

What exactly could be considered as poison?

Things clearly identified as poison were fine and all, so they didn't need to be paid any attention.

But what about mold? Spoiled food?

What about alcohol? It was a first-grade carcinogen and the cause of numerous alcohol-related diseases, after all. Wasn't it essentially just a harmful poison at that point?

The early days of survival after the start of Qing's Wulin journey were about figuring this out.

Mushrooms? Fruit? Grass? Everything seemed fine. 

Even bugs were okay. After eating them a bit, she got used to it.

Except for the disgusting texture, bitter taste, and having to eat a lot to fill herself, it was alright.

Also, it's said to be the food of a protein-rich future, right?

Though this did make her wonder if this really was a suitable alternative food for the future, as well as whether the future world was a place where humans could actually live. 

Ehhh? Even rotten and spoiled food is fine?

From then on, there was no need to fill her belly in the forests and mountains; she could just come down to the city and rummage through trash.

She didn't get any infections either.

As long as they were bound tightly in some way, shape, or form, even deep wounds would heal cleanly without the need for disinfection and such.

And from that, she deduced that perhaps bacteria was also considered poison.

After somehow accumulating enough Practice Points and becoming a bit skilled with a blade, she started catching bad guys, looting their moneybags and collecting bounties from time to time; it was finally her beginning to live a more human-like life. 

And from that, she also realized that alcohol wasn't particularly harmful.

It just made her feel a bit better, without getting drunk enough to lose consciousness. She had no hangover or stomach aches.

She could drink it if she wished and it was fine if she didn't. She couldn't get addicted to it either way.

And ever since the day before yesterday, she had gained confidence in her tolerance to drugs as well.

Now, her rough guess was that if a substance entered her body and had a harmful effect, it was considered poison, thus turning ineffective.

But since there might be exceptions, she couldn't be careless. Just in case.

That was why Qing didn't hesitate to jump in when someone shouted that it was poison. Unlike other things that were ambiguous, she held a certainty that poison would never work on her.    

Qing practically appeared to fly through the smoke.

It was the result of anti-gravity leaps, a technique only possible since the Yue Maiden Footwork had reached the Grand Star.

After scanning through the members of the Advance Blue Brigade scattering into the mountain woods like cockroaches, she found a group of three that she liked very much.

After all, better two than one and better three than two. Right?

It was only upon entering the woods that the enemies noticed their pursuer.

A single girl running like a fluttering butterfly seemed easy for them to handle, so they turned around immediately.

However, contrary to their expectations, a binyeo flew through the air, skewering one bastard's wrist, followed by a bell sound that went Ding, which knocked another bastard down.

The enemy, who had tried to face just one person with two others beside him, now found himself to be the only one left; the look in his eyes was one of urgency and disbelief.

Qing grinned.

"Yeah, I felt like something was missing. My Moonlight Sword……..!"

Was supposed to be starving, but the enemy was already right in front of her. So…

Eighth Move of the Yue Maiden Sword, Infinite Origin of the Moon.

It was the last technique of the Yue Maiden Sword, consisting of five movements in the first half and three in the second.

This sword style was one that aimed for the quickest and shortest path in attacking an enemy. In fact, it had reached the very extremity in such a regard. As such, it slashed three times in a veritable instant and repeated that very instant a total of three times. 

After swinging nine times in an identical manner, the Sword Qi drew crescent moons so brilliant it seemed to actually brighten the earth.

The enemy's wrist was cut, and as the blade returned, the wrist was cut further. Then, it was caught by the subsequent crescents, thus slashed a little more.

Finely sliced pieces poured down in a cascade.

These were cross-sections of the human body; it started from the thin wrist to the forearm, which gradually increased in thickness. Then it moved past the joint to the biceps.

The bastard staggered back, spraying blood.

In that instant, the enemy that had his hand pierced by the binyeo aimed for her side with his blade.

Qing reached out.

A pallid, white hand grabbed his weapon. 

And then, when she squeezed her fist, the blade shattered with a Clink.

"Uh, huh? S-Swordbreaker?"

Swordbreaker referred to a Hand Technique where one broke the opponent's sword with their bare hands.

However, it was originally meant to be a technique where one safely caught and broke the blade; there was no bizarre variation of Swordbreaker where one just crushed a weapon with their sheer grip strength.

If Qing knew this, she might have laughed mockingly at such folly. But she didn't. Why? Because Qing was just as ignorant and foolish.

"No. Moonlight Hand."

The enemy halted for a moment.

\textit{Moonlight Hand? Why? Why not Moonlight Strike? Or at least Moonlight Hand Technique?}

And because of that moment of inattention, he had to pay quite the harsh price.

Pshuk.Qing's hand pierced the enemy's chest.

Her hand, which had sunk in up to the wrist, carefully grasped the enemy's heart. The muscles that moved regardless of the owner's will pulsated, tapping against Qing's palm.

It was the ever so sweet and dulcet rhythm of life.

{\itshape Woah, this works too!

What should I do? Should I try squeezing it?}

"Gurk, kuhhh……."

The enemy made quavering noises, as if he could not breathe.

Agonizing pain surged from the squashed heart, making his eyes roll back to show the whites and foam to form at his mouth.

Qing's lips curled up and she pulled her hand back.

In her grasp was a bloody and bluish mass of muscle. The heart.

For a moment, saliva pooled in her mouth.

Qing unwittingly brought the heart to her lips a-

She was so startled she flung it away.

\textit{Fuck, why am I like this these days?}

Qing furrowed her brows as she retrieved her binyeo from the corpse absent of a heart and stuck it back in her hair.

Qing turned around.

The guy without an arm was still rolling around, holding onto where his limb used to be.

Qing stepped closed, placing her foot on his head.

She pressed down softly at first.

The skull's resistance was firm.

\textit{Ooooh, it can withstand this, huh?}

She applied a bit more force.

Just when it seemed like it was about to crumple slightly, it suddenly burst apart altogether, leaving only remnants of what used to be a head.

A tingle ran from the sole of her foot straight to her head, almost as if there was an expressway in her body that instantaneously delivered the sensation.

Qing was enjoying that lingering resonance when…

"W-Witch……..!"

Qing turned her head.

The bastard who had been beaten down by her Buddha's Palm didn't run away; instead, he was slumped down and spitting out such nonsense.

He has the audacity to say that bullshit? When he gets all startled just because we made eye contact?

"Witch? Want to see what an actual witch is like? Do you like watching talent shows? If you want, I can perform my greatest trick! Showing off organs. How about it? Should I rip out your internal organs and wrap them around your neck? Do you want to try hanging by your intestines and have a make-shift swing? Mmm?"

After shivering momentarily, Qing continued.   

"Now that I think about it, that's a good idea. Mhm. Yeah. Let's go with that."

The bastard's lower garments turned dark in color.

Upon seeing this, Qing's face contorted in disgust.

"Fucking hell. You dirty piece of shit. The fuck is wrong with you? What? Are you scared of me or something? Oh my, oh my. Aren't you supposed to be a man? Huhhh? Even if you die, you should resolve to die with honor. If you are going to hang anyway, you should have already hung yourself. In fact, you should be cutting open your own belly and wrapping your intestines around your neck proudly. That's what a real man does. But what did you do? You were so scared you pissed yourself? Ha! Just chop your dick off at that point. Why the fuck do you have it? Just rip it off! What's the point of carrying something so heavy below if you're the type to sit and pee?"