\chapter{But It Wasn't Like That (1)}

After much deliberation, Daijing Sect Leader Wang Guoru decided to participate in the rescue of the missing persons.

It was not an easy decision.

Though there was apparently a spy within, even without that fact, they were a group capable of evading the eyes of both the Hao Sect and the Beggar's Union.

Moreover, they even had the ability to provide wicked Demonic Arts. 

However, a crisis could also be an opportunity.

Merely attempting the rescue could bring great fame.

Fame translated to influence, and influence to power.

They could potentially become the ruling sect of Huangchuan.

Moreover, all four guests were Masters of the Peak Realm.

There were two such Masters in the Daijing Sect.

At best, the Sect Leader and the Guardian Elder were at the Early Stage Peak Realm.

Including the guests, there were six Masters at the Peak Realm.

Thus, it was a formidable force capable of easily defeating anyone until the Early Stage Transcendent Realm.

For these reasons, Wang Guoru prepared for battle enthusiastically, yet very slowly.

The best case scenario would be the rescue team finding that the mysterious forces had vanished and returning only with the corpses of the missing persons.    

Coming forward with a righteous mind to search for the missing persons would earn them a reputation for chivalry and virtue, and with no enemy, there would be no harm to the disciples.

This was why they prepared slowly and deliberately.

As such, they unnecessarily checked the joint attack formations of the disciples.

And examined the condition of their weapons, giving them ample time to fix and clean them. Then, they rigorously inspected them, before sending them back once again.

They even went out of their way to recount and check the number of ointments and bandages, making strategic delays by sending people to distant physicians for more supplies.

Some might sneer at these shallow tricks, calling them ridiculous, but a sect going into battle was a weighty decision risking their very existence. 

That was why the young Masters of the Heavenly Martial Team turned a blind eye to these obvious machinations.

While the Daijing Sect were fervently acting as if they were busy, the guests had time for some unfinished conversations.

"So, what happened?'

"About what?"

"About Wang Xunwan. That person."

"What about him? He was a bad guy who did something bad. The end."

Peng Daesan's expression crumpled.

"That is not what I am talking about."

"Then what? What's the issue?"

Peng Daesan straightened his face, taking on a grave manner.

"It was too dangerous. That person……" 

Peng Daesan could not bring himself to continue.

Wang Xunwan was in a state hardly recognizable as a human.

If that could be called the form of a human, attaching four sticks into a torso and placing something round on top would suffice in claiming it human as well.

She skinned him alive without killing him and flayed his muscles.

By definition, that was the state Wang Xunwan was in.

Yet, the reality was a much more grotesque and miserable sight.

Every single muscle was slit, cut, twisted, or knotted and some parts completely exposed white bone, thus revealing blood vessels hanging from a distance. 

His chest was cut open, revealing organs that palpitated visibly.

There were many madmen in the world, but even among them, this was a particularly deranged act of cruelty.

"What if you had been subjected to such wickedness? Moreover, you alone, I mean, couldn't you have warned me, no, us beforehand?"

Peng Daesan struggled to even mention such a ghastly incident, clumsily mixing up the subject matter. As such, Qing understood differently.

Qing comprehended that the wickedness referred to Wang Xunwan.

\textit{What the? Were you worried I might have been the one to suffer instead?}

Qing had no intention of hiding her opus.

Had Peng Daesan asked why she did it, she would have simply said there was a bad guy, so she decided to torment him a bit.

Why would she ever hesitate over such actions? There was no shame in them, after all.

However, Peng Daesan, unable to fathom that Qing was the Killing Star who walked among them in these plains under the Heavens, concocted the existence of some evil third-party.

In fact, everyone thought so.

The Daijing Sect Leader believed Qing had rescued his second son.

With Wang Xunwan currently lying bandaged from head to toe, it would take a while for this absurd misunderstanding to be cleared.

Qing laughed at this cute little brother-like concern, pounding her chest.

As expected, it shook heavily, practically sloshing like water.

"You see this body? Late Stage Peak Realm. I do not heed the worries of those weaker than myself."

"You…….! No, no, never mind."

Peng Daesan forcefully swallowed his rising anger.

After all, she wasn't wrong.

Qing was a higher-level Master than Peng Daesan.

And saying a woman should be more cautious just because she was a female could be a great insult.

It was especially so since most female martial artists were sensitive to such remarks.

As such, he silently vowed in his mind.

\textit{I can't put up with this anymore. I have to advance my realm quickly.}

"At any rate, to think he used Heart Absorption Arts. How terrifying."

"Ooh, Changbinie, you know Heart Absorption Arts?"

"That. Uh. Everyone………probably knows, right?"

"What the… It's that famous? Even Sword Friend knows?"

"Of course. Anyone born into the White Path, the Orthodox Faction, should at least memorize the Eleven Great Demonic Arts. It seems Sword Friend is unaware, so I shall take this opportunity to teach you."

"Oing? Ehhh? Why? Do I have to know?"

"Because those wicked things must be eradicated from this world. If found, they must be killed or reported to the Alliance for execution. Thus, anyone claiming to be from the Orthodox Faction must memorize them.

"Seems tough to be orthodox, huh. But, eleven? Usually, it's not numbered like that, right?"

The favorite pastime of the residents of Zhongyuan was lining things up in groups of five or ten. It was practically an obsession for them.

There were Nine Sects plus One Union, as well as the Five Noble Clans and the Ten Noble Noble Clans Under Heaven.

But eleven?

Qing tilted her head in confusion.

Nan'gong Shencai proceeded with his explanation at a moment's notice.

"Firstly, there's the Killer Among Killers, the most dangerous and vile out of all the Demonic Arts. It is called……."

He talked about the Essence Absorption Demonic Arts\footnote{吸星大法; Xi Xing Dafa; Star Absorbing Technique. Originated from Jin Yong's novel 'The Smiling, Proud Wanderer'}.

A dreadfully powerful and horrible Internal Qi Circulation Arts that absorbed others' Inner Qi. In fact, that was not the end of it. This Demonic Art ate not just the Inner Qi but also the lifeblood, essence, and the Innate True Qi of the victim.

And losing one's Innate True Qi, their very lifeforce, meant instant death.

Victims of the Essence Absorption Demonic Arts were found as desiccated corpses, similar to Mùnǎiyī. Upon such discoveries, an emergency would be declared in Wulin, whether they were of the Orthodox, Unorthodox, or Demonic.

For reference, in modern terms, Mùnǎiyī was what was known as mummies.

Leaving the owner of the Essence Absorption Demonic Arts unchecked meant they would become infinitely powerful. The more essence and lifeblood contained within a single body, the more one lost their humanity, thus becoming a monster that hunted only for Innate True Qi.

It was nothing less than the birth of a natural enemy to all martial artists.

"Excluding that, there are the Ten Great Demonic Arts Under Heaven. Along with the Heart Absorption Arts that had emerged this time, there are the Chakra Demonic Tribulation, the Heaven Sundering Blood Reversal Śāṭhya Technique of the Hands, Heart, and Feet, the One Hundred And Eight Asura Sword, Drunken Madness Killing Force, Sky Gazing Killer, Black Slaying Demonic Palm, and Anti-Divine Palm Calamity Dao, no, or rather, Anti-Divine Palm Calamity Half-Sword."

Peng Daesan, who was listening in, growled. 

"When will you stop with that half-sword nonsense?"

"Among the greatest misfortunes of a gentleman, a junzi, is the act of winning someone's favor through cunningly crafted words and subtle facial expressions. A true swordsman does not deceive with words that are pleasing to the ear."

"What do gentlemen and swordsmen have to do with each other?"

"The sword is a gentleman's weapon. A junzi's pride. That is what being a swordsman means."

It meant he intended to continue with his current path.

Qing was counting on her fingers as she listened.

She showed the two fingers she had left.

Peng Daesan sighed deeply and informed her of the remaining two.

"Purple Lightning Demonic Arts and White Hand Demonic Arts."

"Oing? Hehhh?"

Why did such a familiar name come up among all that filth?

{\itshape Wasn't it the martial art recommended by Zhugeie?

Did Zhugeie give me one of the Ten Great Demonic Arts?}

If Zhuge Ihyeon heard this, he would jump up in astonishment. 

He could never have imagined Qing would learn just because he told her about it. Furthermore, he was definitely about to warn her.

It was just that he was cut off in the middle.

"Uh, are the Ten Great Demonic Arts……..really that bad?"

"Is that even a question? The nature of Demonic Arts is such that the more they are used, the more Demonic Nature infuses into the practitioner, causing them to lose the heart of a human. They become increasingly cruel and lose patience. That means a Demonic Human is born."

"But there could be exceptions, right?"

"The reason why the Ten Great Demonic Arts are designated as such is one of two reasons. Either the process that the demonic practitioner needs to go through to achieve results is terribly horrific or the martial art itself is extremely dangerous for a Demonic Human to possess."

"Then, what about the White Hand Demonic Arts?"

"Is that the only one you've heard of?"

Peng Daesan sighed yet again.

How could one navigate such a perilous Wulin in such ignorance?

"The White Hand Demonic Art is dangerous because it is too powerful."

The danger of the White Hand Demonic Arts laid in its unique Qi Wave, a penetrating power called the White Hand Drought Poison.

If a practitioner's hand burrowed into the body, the Inner Qi that had qualities of a Drought Poison infiltrated, thus twisting, tearing, and bursting the meridians. 

If it reached the Innate True Qi, it jeopardized health and lifespan, leaving the victim bedridden.

This was a common trait of martial arts derived from the White Hand Demonic Arts.

Some examples included the Blood Hand Demonic Arts or the Flame Demonic Arts.

Qing internally broke out in a cold sweat.

{\itshape What the fuck is this, huh? Getting caught means I'm fucked.

It's a bit much to kill someone just because they mastered a bit of martial arts, no?

Despite all that fuss, saying ‘DemonicArtsDemonicArts' or whatever…

It's hard to understand the mindset of these ling longs. Maybe it's because they're the OG ching chongs?}

Apart from that though, there was also a sense of pride.

A martial art feared because it's so strong!

{\itshape Who am I, you ask? Yeah, that's right. I'm the owner of the White Hand Demonic Arts.

I guess Zhugeie did recommend one helluva martial art, huh?

As long as I don't get caught, it'll be all good, won't it?}

Dead villains tell no tales, after all.

"Have you heard anything about those ‘bad guys'?"

"I dunno. But I did hear that the people who went missing never returned."

"Hm."

"There are some punks that I have in mind, you see?"

Qing briefly shared the incident she had at Dongting Lake.

A crazy woman creating Jiangshi had been masquerading as an Enforcer for the Wulin Alliance and the Demonic Cannibal appeared.

Then, Ta-da! The incredibly strong Qing made her appearance, defeated the Demonic Cannibal, and saved everyone.

"Wait, Sword Friend. Did you just say you killed the Demonic Cannibal?"

"Of course. On top of that, I won a whopping one against six. I really am quite something."

"Oh, oh, Sword Friend! Indeed, all the great deeds of this world unfold from the blade of a swordsman! Well done, Sword Brother! Well done!"

It was the plain truth.

After all, strictly speaking, weren't the five kid Jiangshi also on the Flame Demon or whatever's side?

While watching Qing's boasts, Peng Daesan snorted with laughter.

"It must have been you who were the six."

"Well, yeah. I guess that's true. But how else could I have defeated a Transcendent Master who pumps out Qi Force like that?"

Qing stood proud. She wasn't ashamed at all.

Then, Changbin, who had been listening quietly to her story, timidly offered his opinion.

"Excuse me, so, does that not mean we are about to walk into a place where such villains are at work? Perhaps it would be best to request assistance from the Allian-"

Qing frowned at Changbin.

And then, she was about to persuade him that those left behind, unable to let go of the lingering regrets due to their missing loved ones, would essentially be throwing away their lives along with them. However…

"Young Lady Ximen? If that is the lens you wish to look through……. It is not that I oppose the rescue, but…….. Ahem, well, since we already have several Peak Masters here……."

Changbin's rebellion was promptly squashed.
