\chapter{But It Wasn't Like That (5)}

Despite the terrifying verbal abuse, the Advance Blue Brigade member didn't even properly hear it.

He was one who had pride in being a member of the Heavenly Demon Divine Cult.

The Divine Cult was a place where the strong prevailed, where the law was the survival of the fittest, thus making it a melting pot of madness filled with crazy bastards and bitches.

A bastard who ate people? Yep, they existed.

A bastard who tortured people? Yep, they existed.

A bastard who enjoyed killing people? Of course, they existed.

However, having directly encountered and dealt with various Demonic Humans, he had actually developed an eye for spotting such evil types who couldn't necessarily be considered human.

The girl in front of him was one of them. No, she was the real fucking deal even amongst those lunatics.

It was unclear why such an existence was hiding within the Orthodox Faction. She was worse than any Demonic Human, no, it was as if she was a being of a different species altogether……. His jaw trembled in terror.

"Please spare me…….."

A First-Rate Master rubbed his hands together so quickly that he was practically vibrating like a fly.

This was one of the strong suits of the Unorthodox Faction.

After all, a martial artist without a grand cause would value their own life above all else.

Qing looked down at the man groveling before her.

He was someone who she could kill, just like the other bastards.

Qing's gaze turned cynical, clearly biased against him.

"Me? Why should I?"

"If you spare me, I'll do anyth-"

As Qing took a step forward, the man screamed in horror.

"Wait! O Great One! I have information! I will tell you everything I know! Bokshinjeok! We are looking for Bokshinjeok!"

Qing stopped moving.

She didn't know what Bokshinjeok was, nor was she curious.

However, the Status Window that popped up in front of her seemed to think differently.

The Mission Window of [Omen, (Unknown)th Crisis]burst into flames and displayed an entirely new sentence.

\begin{quote}

[Divine Cult Under The Heavens, War and Chaos of the Demonic Cult. The Beginning CHAPTER. (Unknown)th Crisis]

Description:[You can track an important Divine Relic of the Divine/Demonic Cult. With it, you can join the Divine Cult or steal it to become the Great Adversary of the Demonic Sect.]

Obtain more information about Bokshinjeok
\medskip

Lone Jianghu Journey) Steal Bokshinjeok

Demonic Cult) Deliver Bokshinjeok to the Wulin Alliance

Heavenly Demon Divine Cult) Deliver Bokshinjeok to the Divine/Demonic Cult

Heavenly Slaughtering Star) Steal Bokshinjeok

[This choice could influence everything below Heaven.]
\end{quote}

"Ssssp…….."

{\itshape It's you again, Lil Window?

An ex who asks, ‘Are you sleeping?', at 2 AM would be smoother with it than you.

How am I supposed to accept you when you're just soooo fucking clingy?

Why don't you just go die in a hole?}

Suddenly, the Strategy Guide she had read half-heartedly came to mind.

{\itshape Wasn't it said that to progress through the game, one must resolve three random crises in the Early-Game, Midgame, and Endgame?

But I've already seen the Final Crisis and the Final Boss, you know?

What kind of fucking order is this? What an actual shitfest.

Would it end if I just beat Yun Yuanling?

Or do I have to deal with all three of them when one is already too fucking much?

But still, the Mission Window was somewhat manageable since the coincidental meet-up with Uhnyeong, I think?

At least it doesn't eat away at my brain like the Martial Arts Window.}

"Haaa……"

Qing let out a deep sigh.

She wanted to clear these choked up feelings right away, but…

"So, what's up with this Bokshinjeok thingy, you fucker? Why are you talking about shit that only you know? That's illegal according to that something something blah blah blah law, you know?"

Qing continued speaking with a crooked posture, akin to some gangster.

"Then, my verdict will be the death penalty."

"I shall tell you!"

Two hundred years ago, there was a legendary blacksmith called Banchi, known as the Incarnation of the True Lord of Virtuous Fire1……….

Qing threw a tantrum, annoyed at the exposition.

"Shit, what's with this sudden boomer-like story? What are you going to say next? That the only possession he had was the bundle he carried around? Is this really the time for you to be telling old stories about some grandpa? Do you want me to knock out all your teeth so you become a grandpa too?"

"N-No! So like……."

One of Banchi's masterpieces was a flute made of Ten Thousand Year Cold Iron, Bokshinjeok.

"The fuck? You guys caused this fucking shitfest just for some flute?"

"It is not just any flute. It is a flute made of Ten Thousand Year Cold Iron. It is a treasure desired by all artists in the world, with a sound so beautiful that even the Green Emperor praised it……."

In ancient China, the Green Emperor, Fuxi, was considered something like a supreme deity who played a role in the creation of humanity.

He generously bestowed all sorts of knowledge to humans, including, of course, music.

The phrase that even the Green Emperor would praise it was the highest compliment that could be given to an artist.

But if one told Qing, ‘There's such a flute flute and it has a beautiful tone which surpasses all sounds of nature'...

She wouldn't be interested because she couldn't even imagine what kind of flute it was. So, why should she care?

She would just say, "Okay, sure. But isn't it just a flute?".

However, if one told Qing-

"That flute is a treasure worth ten thousand gold………"

-Something like that…

"It is a treasure! You're correct! I acknowledge it."

-was what she would exclaim in admiration.

Ten thousand gold? It was an unimaginable amount of wealth.

If it was that much, it made sense to Qing why the Mission Window was making such a fuss.

Qing pondered.

Either way, she couldn't just let this group of bad guys have it.

But that didn't mean she could entrust it to the Wulin Alliance either.

Wasn't the Final Boss, Yun Yuanling, serving as an Enforcer or whatever for the Wulin Alliance?

Dropping a treasure into such a loosely managed organization would mean it would disappear without a trace.

{\itshape Then, what should I do?

Master occasionally played the flute.

She would probably like it if I gave it as a present, right?}

Qing made up her mind.

"What are you doing?"

"Y-Yes?"

"Don't you know, ‘Starting directions'\footnote{GPS startup voice}? What are you even doing? Hurry up and guide me."

"Then does that mean you will spare……."

Qing's eyes narrowed.

"What the fuck. Is a villain……. talking back to me right now?"

"I will guide you! I want to guide you! Please let me guide you!"

Qing relaxed her expression.

"Nice, nice. Very good. Let's go."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Hundreds of drawers were scattered across the floor of the burial chambers.

Rotten pills, rusted binyeos, and ornaments of mere emeralds, as well as decayed changdaos4 and daggers, were all mixed together, rolling around.

It was unimaginably malicious to think that the last part of the treasure map was to furiously pull out drawers.

Originally, it was not a job for the boss of the Advance Blue Brigade to do personally, but there was no choice when a fire was roasting right beneath his ass.

Exactly how long had the fearsome Demonic Adepts of the Demonic Sect been rummaging through the drawers of the burial chamber?

Finally, a drawer containing a dark blue flute fell to the floor from the highest shelf; a location so fucked up that it had to be pulled down by hanging on it.

"We found it!"

"Finally……..!"

Yeom Saraedal let out a voice full of emotion as his lifeline finally revealed itself.

The dark blue body, one and a half feet in length, looked like a metal club at a glance, but it was actually an invaluable treasure.

"Very well, now……."

It was then.

Thud. Someone jumped into the burial chamber.

Yeom Saraedal grabbed his mace5 in startlement.

"Who is it?! What the. Nevermind. It's you. Where are the others?"

Yeom Saraedal recognized the face of his subordinate.

He couldn't remember his name.

But the face was at least familiar.

The subordinate fidgeted in hesitation.

"Um, well, about that………"

-Yo, is this the right place? I'm coming down, okay?

Suddenly, a lively voice penetrated the stone chamber.

At the same time, Tap. A charming girl in the flower of maidenhood landed with a light step.

Qing looked around the stone chamber.

In the center, an opened stone tomb revealed faded silk and the remnants of a decomposed body underneath.

Furthermore, the floor was littered with drawers that had been pulled out.

"What's this? Grave robbing? You're tryna dig up a tomb? You evil bastards! How dare you disturb the peace of the dead! This is unforgivable!"

Yeom Saraedal glared at his subordinate, clearly asking for an explanation.

Qing also looked at the man with wet pants.

The subordinate alternated his gaze between the boss and Qing.

Then, he naturally drew his sword and aimed it at Qing.

Qing frowned.

"You're going to betray me here? Seriously? Is that really the best you can do?"

"Shut up! It was just to lure you here!"

"Oh well. Whatever. I had no intention of letting you live anyway……."

Qing never promised to spare him.

Now that she had reached her destination, she was ready to send those worthless villains to the end of their journey. The afterlife.

\textit{Look at this bastard. Quick on the uptake, huh?}

"Now then! Cry out, Moonlight Demon Slaying Dao! Moonlight Demon! Slaying Half-Sword!"

Qing charged forward, spouting any words that came to mind.

Yeom Saraedal swung his mace in response.

Clang! Blade and metal collided, producing a loud noise.

Yeom Saraedal's complexion turned pale.

\textit{How does this brat have such Inner Qi……!}

For reference, Yeom Saraedal was already drained from breaking the ceiling of the stone chamber.

"What are you doing, standing there?!"

At Yeom Saraedal's shout, the remaining four members charged.

Qing parried a sword and a dao, then stuck out her butt.

The blade of a spear barely grazed the front of her pelvis.

And then, she lifted her sword high.

It was then.

Shrrrk, the sound of metal sliding.

Iron chains wrapped tightly around Qing's forearm.

It was a weapon called a chain whip6 in Zhongyuan.

"Now!"

The one with the chain whip yelled.

Yeom Sareadal, not missing a beat, swung his mace with all his might.

\textit{I will smash that skull in an instant!}

A vicious mass of iron, bristling with spikes, headed straight for Qing's head.

Qing pulled her arms back aggressively.

Due to the combined force of Qing's monstrous strength and Inner Qi, the owner of the chain whip flew through the air, inadvertently becoming Qing's shield.

THWACK! The one holding the chain whip blocked the mace with his back.

His spine shattered in an instant, causing him to spew blood and die from that single blow.

At the same time, Dinggg-! The sound of a bell resounded out of the blue.

The upper body of the one wielding the dao exploded, scattering the entrails inside all around.

A thrilled voice filled the chamber.

"Half-Sword. Eliminated!"

"You bastard!"

But after so boldly shouting out, he hesitated. It was because he clearly realized that Qing was not someone he could easily deal with.

"Bastard? That's no way to speak to someone you just met. It's informal. And rude. Don't you know what manners are? Ah, it really shows how you weren't taught well. Oh, well, if you're so pressed7, then… You know, right?"

Qing bent her finger, beckoning him.

Yeom Saraedal made eye contact with the last remaining subordinate.

At the same time, he quickly folded a few of his fingers and straightened them, making a shape. It was a secret signal among the brigade members.

It meant to attack simultaneously.

The subordinate briefly lowered his gaze then lifted it again.

It meant that he understood.

And then-

"Now!"

Yeom Saraedal roared, channeling all his True Qi into his feet and stomping the ground.

The subordinate, too, knew that this was his last chance and kicked off the ground, leaping upwards.

Both of them flew towards the hole in the ceiling.

It was as if they had pre-arranged a dramatic act of mutual betrayal.

Truly a specialty of bad guys.

Since the hole was narrow and both jumped at the same time, they inevitably collided in mid-air.

Then, they fell to the ground, tumbling around.

"You bastard! Didn't I tell you to attack! How dare you defy orders!"

"I should be the one saying that, Boss! Why are you running away?!"

"This is insubordination! And insubordination is punishable by death! Death!"

"You're the son of a bitch who tried to abandon your subordinate and run away! What kind of fucking piece of shit are you?! I knew you were like this from the very start! A fucker calling himself the boss when all he does is fuck around all day! What a fucking joke!"

"W, wh, what the fuck did you just say to me, you dogshit motherfucker!"

They both raised their voices at each other.

Qing made a face.

\textit{What are they again? The Demonic Cult? Anyway, whatever they're called, seems like they're dysfunctional.}