\chapter{Even In Dreams, Wishes Are Slaughtered (1)}

The highlight of any trip is undoubtedly the culinary adventure.

Traveling to a new land and tasting dishes you've never imagined before is the essence of exploration.

However, these unimaginably new dishes often come with their own risks.

The Pasachung Festival!

Pasachung, insects that live in the fine sandy bottoms of clear streams, are also known as Sutosam or Chungsam.

They're called "water ginseng" or "insect ginseng" because of their health benefits.

There are many ways to cook Pasachung, but the most revered method is to blanch them in boiling oil, steam them thoroughly, and serve them in their original form.

This preserves their color and shape, making them look exactly as they did when alive—though only on the outside.

Each insect has its innards and tough blood vessels meticulously removed, a process that requires the skill of multiple seasoned chefs. It's the pinnacle of culinary artistry.

As the server passionately explained, Qing's impression of the finest Pasachung dish, the "Majestic Pasachung Feast," was this:

Hmm. Earthworms.

Gejiu is famous for its high-quality Pasachung, so over half of the dishes here feature them.

However, most dishes remove the heads, tails, hard shells, and legs, making them look like sliced meat.

But when a dish is served with the insects' original shape intact, as if to say, "This isn't meat, it's earthworms," it's hard not to feel uneasy.

Why? Why go to such lengths to preserve the original form? Is this some kind of twisted joke?

Actually, Pasachung aren't earthworms.

They're the larvae of dragonflies, with no relation to earthworms, but their appearance is strikingly similar.

Qing can eat anything, but that doesn't mean she'll eat just anything.

While she's not picky, half the enjoyment of food comes from the memories attached to it.

Bad memories associated with food can ruin even the most exquisite dishes.

Insects are something Qing can't enjoy eating.

Hmm, can't we just have regular meat—beef, pork, chicken, lamb, goat, pheasant, or duck?

At that moment, Tang Lan-Ah reached out with her chopsticks.

She picked up one, examined it carefully, and then popped it into her mouth.

"Oh, this. Not bad for such a remote countryside."

Tang Lan-Ah, the Sichuan Little Villaines, had a refined palate.

Having grown up eating only the finest delicacies as a true power player in Sichuan, her approval carries weight.

A dish acknowledged by Tang Lan-Ah as a masterpiece!

"Here, Qing. Try this. It's medicinal, so the flavor is just okay, but the seasoning is quite good."

Indeed, Pasachung is also eaten in Sichuan.

It's just that winter is the peak season, so it wasn't served when Qing visited.

As Qing hesitantly picked at the dish, a rare sight unfolded.

Peng Daesan and Zhuge Lixian exchanged glances.

Their serious expressions and intense gazes prompted Peng Daesan to tap the table lightly, and Zhuge Lixian nodded subtly.

Were the two men conspiring?

Well, calling it a conspiracy would be unfair.

They were simply voicing concerns they felt needed to be addressed as friends.

"Qing."

"Huh? What?"

"Wasn't that a bit too much?"

"What was?"

"The Zheng Family Estate master. Many merchants in Zhongyuan talk about business ethics, but few actually practice them. From what I saw, he didn't seem like someone who deserved such harsh treatment."

Someone needed to rein in this recklessness, and the two men had come to an agreement.

'Among this group, only we—and perhaps even within the Half-Sword Double-Saber Association—could do so, along with Lady Gongsun.'

Qing blinked.

Just as she was about to speak—

"What? Are you saying our Qing should've flattered some lowly merchant? Where does some scummy merchant get off acting so arrogantly in front of a distinguished guest? He should've been groveling in the dirt!"

Tang Lan-Ah's eyes flared with anger.

\textit{I shouldn't leave Ciyu with Lan-Ah alone. She'll turn our precious girl into a monster…}

Peng Daesan's expression soured.

"Now, now, Lan-Ah, calm down. San is just too naive. Innocent. Pure?"

There's always a higher heaven and a deeper hell, and Peng Daesan's expression was the epitome of that.

"Isn't it suspicious? With the plague causing such chaos, using the cure as bait to lure people in? And then suddenly treating them so well? Why?"

"Didn't the Zheng Family Estate master explain that?"

"No, it doesn't add up. Why deceive them in the first place? If they needed miners for the new coal mine, why not just say so? Why go through the trouble of hiding it and even bringing in women?"

"It's a coal mine, after all. It's understandable they'd want to keep it hidden from local officials or nobles who might covet it."

"Hidden? When we asked before arriving, everyone in the city knew about the young master from Hangzhou who struck it rich with an orchard and discovered the coal mine."

"Hmm."

"And San, you might not know, but providing three meals a day with plenty of meat, comfortable beds, and generous wages? If they'd just recruited normally, they'd have had a line of applicants stretching around the city walls seven and a half times."

Qing, who'd experienced the life of a beggar in her first year in Wulin, knew this well.

With such a good job, everyone would flock to it. If a beggar dared to apply, it'd be the day they'd kill a beggar.

In professional terms, it's called 'kicking down the ladder'!

That's why beggars couldn't find jobs and had to keep begging.

What? Yunnan people are laid-back and lazy?

With such top-tier treatment, word would spread, and miners would come flocking like clouds.

"Besides, for such a ruthless recruitment method, their approach was surprisingly sloppy. Even if it weren't us, someone like the masters of the Diancang Sect or even Tai Ping himself could've easily found out and come here."

It's as if someone wanted to use the cure as bait for human trafficking, only to reveal, "Ta-da! It's not what you think!" and show off their twist.

It's all too perfectly crafted.

"Hmm."

"And did you see how he acted? How could a merchant be so bold in front of martial artists, armed bandits? Shouldn't he have been at least a little intimidated?"

Zheng Liuzhang's demeanor was too calm.

When we insisted on seeing the master, he didn't even seem curious about the identity of the "wandering swordsman."

"And as San said, this might be a bit prejudiced, but there can be kind merchants, right? But kind wealthy merchants? When someone makes money, someone else loses it. How could someone so young amass the fortune to build such a grand estate and run businesses in a kind way?"

On top of that.

\textit{His evil karma was a staggering twelve hundred points.}

\textit{Twelve hundred!}

\textit{Isn't that suspicious?}

\textit{After hearing and seeing everything, could I just say, 'Ah, he's a solid young man, I misunderstood,' and walk away?}

Peng Daesan was at a loss for words.

Listening to this, it really does seem suspicious.

But still, something felt off.

Feeling wronged, Peng Daesan shot a glance at Zhuge Lixian.

He's smart despite his talkativeness, so maybe he could find a flaw in Qing's reasoning and add his own thoughts.

At that, Zhuge Lixian opened his mouth as if he'd been waiting.

"Indeed! I'm truly impressed. And moreover, no matter how high the quality of the coal, paying such high wages would make it hard to turn a profit. There must be another motive."

Peng Daesan's eye twitched.

\textit{This guy, betraying me now?}

"See? Even Zhuge thinks it's suspicious. San, you're just too naive."

"Ugh."

"Oh, our San. Being so naive and soft-hearted, how will you survive this harsh Jianghu? I'm really worried."

"Ugh…!"

Peng Daesan felt wronged.

Of course, he would.

It's not that Qing is particularly smart, but she'd already decided on her conclusion and built her suspicions around it.

\textit{Twelve hundred points of evil karma—that's not something you can just dismiss as a misunderstanding.}

\textit{If he's truly a bad person, he deserves to be dealt with in the most horrific way.}

\textit{If he's been deceived into accumulating twelve hundred points, we need to find the root cause and correct it, not just let it go.}

And Peng Daesan felt even more wronged.

\textit{Zhuge Lixian, this bastard…!}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In a room adorned with dazzling silk threads hanging from wall to wall, a young boy sat on a raised platform, puffing on a pipe.

The red embers glowed, and green smoke billowed from the middle-aged man's mouth.

As the green smoke slowly rose and dispersed, a massive silk tapestry with golden embroidery was revealed.

The tapestry depicted five creatures—a centipede, snake, scorpion, lizard, and toad—locked in a fierce battle.

These five creatures are Zhongyuan' most notorious poisonous beings.

Thus, they're collectively called the Five Poisons.

And the group that bears this emblem is one of a kind.

The Five Poison Sect!

This was the Five Poison Sect's main hall.

But something was strange.

The main hall's highest seat, where the sect leader should sit, was occupied by a young boy?

Even more bizarre was the middle-aged man kneeling respectfully before him.

The man known to the world as the Five Poison Sect Leader, Hou Tianchi.

As the boy continued puffing on his pipe, a woman suddenly appeared and whispered in his ear.

Hou Tianchi was startled, but the woman, with her waxen white face, smiled faintly and disappeared in the blink of an eye.

"No need to worry. She's already dead."

"A ghost, you mean?"

"Something even more than that. Hmm."

The boy took another puff and exhaled green smoke before speaking again.

"Hou Tianchi."

"Yes, Poison Demon. What is your command?"

Poison Demon!

The shocking identity of the boy!

If anyone else had been present, they would've gasped in shock.

Of course, if Qing had seen this, she'd have said, "Poison Demon? Who's this kid acting all high and mighty?"

But according to the rules of Zhongyuan nicknames?

Two-character nicknames are reserved for the strongest, acknowledged by the world.

One could roughly guess how terrifyingly strong someone with such a nickname must be.

But for that person to take the form of a young boy was bizarre.

Or perhaps it was a classic case of self-given nicknames gone wrong.

A disease where one's own standards of coolness clash severely with the general consensus.

The Poison Demon took another puff. Then, exhaling:

"A guest is coming. A very ill-mannered one at that."

A soft giggle echoed from somewhere.

Hou Tianchi turned his eyes and caught a glimpse of the woman's robe disappearing behind a pillar.

Something even more than a ghost? Hou Tianchi felt a chill run down his spine.

"With the grand plan underway, I'm concerned about unnecessary trouble from this guest. But we can't exactly refuse to receive them."

"I'll go greet them."

"You'll find it quite amusing. It seems there's a woman from the Tang family among the guests."

At that moment.

Hou Tianchi's eyes burned with murderous intent.

The Poison Demon smiled contentedly.

\begin{lstlisting}
	The chapter's title is another reference of 1947's South Korean song, '우리의 소원' (Our Wish)
\end{lstlisting}