\chapter{Even In Dreams, Wishes Are Slaughtered (2)}

The leader of the Five Poisons Sect, Hou Tianchi, was truly poisoned.

This wasn't a metaphor—he was literally poisoned.

Grotesque lines etched across his exposed skin, a phenomenon caused by the deadly poison coursing through his veins.

A Poison Master!

Hou Tianchi had reached the realm of a Poison Master!

It was the ultimate realm that every master of poison arts aspired to achieve.

However.

Hou Tianchi wasn't particularly proud of it.

This realm wasn't attained through his own efforts; it was merely a half-baked achievement, achieved through sinister methods.

In fact, because of this, he could never truly ascend to the genuine realm of a Poison Master.

But he had no regrets.

Because there was something he had to do—revenge he had to exact.

During the failed mission in Sichuan, a generation of disciples from the Five Poisons Sect had perished.

And they had died horribly at the hands of a vicious demon.

A generation of disciples—those who were like his own children, the sect's core members—had been massacred. What kind of master wouldn't be consumed by hatred?

His greatest enemy was that vicious demoness, Ximen Qing, who had ruined everything.

His second enemy was the wicked Tang family of Sichuan.

His third enemy was Zhongyuan itself, the invaders who had dared to steal the land of his people.

So when the Blood Cult extended its sinister hand to the Five Poisons Sect, Hou Tianchi gladly took it.

And now, his second enemy was walking right into the territory of the Five Poisons Sect.

The child of the Tang family—the most beloved child of the family, Tang Lan-Ah.

Moreover, it seemed that his greatest enemy, Ximen Qing, was accompanying her. Though he couldn't be certain because her face was covered, there was no need to ponder who the three-headed swordswoman traveling with the Tang family's daughter could be.

A cold, poisonous aura emanated from Hou Tianchi's eyes.

It was the deadly poison of a Poison Master, rising like a sinister mist from his eyes, nose, ears, and mouth, scattering into the air.

Hou Tianchi gritted his teeth and growled in a rough voice to the person beside him.

"Is the Ten-Sided Ambush plan ready?"

The Ten-Sided Ambush plan!

This was a strategy from the historical tale of the Chu-Han Contention, where the great warrior Xiang Yu faced off against the first emperor of the Han dynasty, Liu Bang.

The target was Xiang Yu and his army of twenty-five thousand.

The ambushers were ten commanders leading ten armies, totaling three hundred thousand troops.

With over ten times the number of troops surrounding from all directions (ten sides), and countless ambush points set up to observe the enemy with eyes and ears.

No great general in the world could escape this death trap.

Except for Xiang Yu. Xiang Yu broke through.

Since only Xiang Yu survived, it's debatable whether the Ten-Sided Ambush was a failure, but since the goal was to kill Xiang Yu, it was indeed a failure.

In fact, the Ten-Sided Ambush was a later creation.

(Of course, Xiang Yu was indeed a madman who could break through an army twelve times his size with sheer force.)

If you asked Han Xin about the Ten-Sided Ambush, he would likely explode in anger.

'What? You think I came up with such a plan? No, what, do I look like a pathetic fool who needs a strategy to face twenty-five thousand with three hundred thousand troops? With an army twelve times the size, what strategy is needed? Even if a dog held the command baton, we'd still win.'

In fact, with three hundred thousand troops against twenty-five thousand, no grand strategy was needed.

In fact, with three hundred thousand, you don't even need swords or spears.

Later, the original ancient strategist Zhang Liang, who played the role of Zhuge Liang in Chu-Han Contention, had the three hundred thousand troops sing simultaneously, creating a cacophony of noise.

This caused severe psychological damage to Xiang Yu, who ended up taking his own life.

This is the famous 'Song of Chu from Four Sides' strategy!

The strategy of Chu songs coming from all four directions.

After all, who could maintain their sanity when noise from all directions—above, below, left, and right—echoes around them?

Xiang Yu survived the three hundred thousand troops of the Ten-Sided Ambush, but he couldn't survive the noise!

This also highlights how serious the issue of noise pollution is.

Anyway.

The Ten-Sided Ambush plan is a ruthless strategy to encircle and annihilate the enemy, aiming not for surrender but for complete destruction.

In other words, it's an encirclement and annihilation formation!

This was also the true nature of the 'welcome' the Poison Demon had mentioned.

One might wonder why they didn't just stay at the Five Poisons Sect's headquarters and wait.

But if the Tang family's daughter died at the Five Poisons Sect halls, it would cause a huge problem.

If it were discovered that they were involved with the Blood Cult, they would immediately be attacked by the Orthodox sects, and the Blood Cult also had its own agenda, so that would be troublesome.

However, disappearing without a trace on the road is a tragic but entirely possible event.

Thus, preparations for the welcome were well underway.

But asking about the progress of the ambush preparations eight times in a single shichen (two hours) was a bit excessive.

"Brother, please wait a little longer. You can't drink soy milk just because you're in a hurry for tofu."

You have to filter and solidify soy milk to make tofu; it doesn't become tofu just because you're in a hurry.

Being in a hurry won't make the tofu solidify faster, so rushing won't help—just wait patiently, as Zhongyuan saying goes.

"Aren't you anxious at all? Those enemies could show up at any moment."

"I also want to tear those bastards apart, Brother. But you've been awake for two days straight. You need to stay alive to exact revenge, or you'll collapse first."

"Every time I close my eyes, I see my disciples. They're crying tears of blood, begging me to avenge them. How much of the formation is complete? The poison? Has the blood poison the Blood Cult promised arrived yet?"

"You've been asking every moment, Brother. Trying to eat hot tofu will only make it harder."

If you're in a hurry, you can't eat hot tofu.

In Qing's hometown, this corresponds to Zhongyuan saying, 'The more you rush, the more you would take a detour'.

"We need to hurry. Not a single ant should escape. Those bastards, damn it, even eating them alive wouldn't be enough—"

"Rushing will only backfire. Fermented tofu needs to be fully fermented; if it's not, it's just spoiled tofu—"

"Enough with the tofu! Stop talking about tofu! Ugh, I need to look around. With the sect's enemy crawling right into our territory, why aren't we moving faster? How, how—"

"Oh, please…"

It seemed the Five Poisons Sect disciples wouldn't be getting any sleep tonight.

With the resentment of lost sleep fueling them, they would have to prepare for the terrifying Ten-Sided Ambush and the welcome.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the middle of the night.

Somewhere in the mountains, the Five Poisons Sect disciples were sweating profusely as they dug traps, set up formations, and prepared ambush positions.

Meanwhile, Qing and her companions were also out for a night stroll.

The night clothes of Zhongyuan were pitch black.

Common sense would dictate that night clothes, meant for wearing in the dark, should be white, yellow, or fluorescent to avoid major trouble in the night.

After all, in the pitch-black night, wearing pitch-black clothes, how could anyone see anything?

But in the current Zhongyuan, in this era, humans had yet to conquer the night.

Night was for sleeping, and there was no reason to go out in the first place.

So those who ventured out at night were almost always thieves, and thus night clothes naturally became pitch-black outfits for thievery.

And Qing was currently wearing such night clothes.

With her chest tightly bound, the fierce aura of the Three-Headed Swordswoman was nowhere to be seen, replaced by the figure of a tall thief.

"Shit, it's a bit hard to breathe. It's too tight."

As she tugged at the bandages around her chest, Peng Daesan and Zhuge Lixian awkwardly averted their eyes.

But why the sudden need for night clothes?

Was she suddenly declaring that her true calling wasn't being a martial artist but a thief, and now she was switching professions to become a thief?

Of course, that wasn't the case.

Because Qing had always been both a martial artist and a thief—she was originally a thief.

Not just any thief, but a great thief, the successor to the legendary Divine Thief.

Unlike previous Divine Thieves who stole the wealth of evildoers, she stole their lives, but in any case, stealing something from evildoers to benefit the world was the spirit of the Divine Thief, right? (Of course not.)

"See? I told you it was suspicious."

Down below, around the coal mine of the Zheng Family Estate, several red torches were lit, slowly moving around.

Just like the principle of night clothes, there was no reason for an ordinary mine to have torches and guards patrolling in the middle of the night.

Especially since the mine was still under development and not yet in full operation.

And if the mine was a coal mine, where even the smallest spark was dangerous, and expensive glass lanterns were used in this flammable den, even more so.

"Anyway, I'll be back. You didn't have to come this far with me."

Qing waved to her friends crouched in the bushes on the mountainside.

Through the only hole in her mask, a beautiful crescent moon appeared horizontally.

They had followed her, saying they'd help if anything happened, but, well, what help could these amateurs really be? Still, their intentions were commendable.

Even a blank sheet of paper is lighter when carried by two, though carrying a single sheet of paper with two people is actually more inconvenient.

\textit{But in case of emergency, they could be of help, so, well, it's reassuring, I guess.}

It wasn't difficult to get past the torch-bearing guards and head toward the coal mine.

The teachings of the current Divine Thief, Tian Youxue.

Don't think it's difficult just because there are many guards.

In fact, places with strict security are less likely to be targeted by thieves.

Since thieves wouldn't come anyway, the guards tend to become complacent, so it's better to boldly move forward.

Exploit their psychological weaknesses.

Moreover, torch-bearing guards were even more vulnerable.

Torches are never light, and even if they're not heavy, holding them up for the entire shift is no easy task.

In the end, the guards had no choice but to lower their arms and hold the torches forward.

And in the darkness, a torch held forward is more of a hindrance than a help.

When there's a bright light in your vision, the dark areas become even darker and harder to see, and humans are naturally drawn to look at the light.

So how could they possibly spot Qing slipping behind the flashy miner's quarters and various tents?

Especially when she was a master of stealth, moving without a sound.

Thus, she reached the mine entrance without much difficulty.

However, the two guards stationed at the mine entrance were quite disciplined.

But even this had a solution.

Qing immediately climbed the cliff.

With the footwork of the Divine Thief, which could pierce even steel, she climbed the rocky cliff as if it were tofu, effortlessly scaling it without needing any protruding rocks.

After climbing for a while, she moved sideways.

Then, sliding down the cliff, she finally reached the top of the mine entrance.

Humans don't have eyes on the tops of their heads, so they can't see what's above them.

And who would think to look up while on guard duty?

Qing, clinging upside down to the mine's ceiling, quietly moved inside.

After moving quite a distance and the surroundings became completely dark, Qing finally landed on the mine floor with a soft thud.

\textit{Mine infiltration, complete. Easy, right?}

The pungent smell of coal seeped into her lungs.

\textit{Unpleasant, yet somehow familiar and oddly comforting—why is that?}

Qing didn't know, but this was the scent of civilization.

The lingering scent of internal combustion engines, something city dwellers like her had grown accustomed to without realizing.

Qing moved forward without hesitation.

The outside security was strict—or at least pretended to be—but the inside was eerily empty, with no signs of life.

After all, the darkness itself was sufficient security.

After moving a considerable distance from the entrance, the world was pitch black, with nothing visible.

Qing's body was beyond human, her night vision surpassing that of humans, almost like having night vision goggles built into her eyes.

But even this required at least a faint light source to see; complete darkness was beyond even her.

But Qing had a solution.

A faint starlight emanated from her hand.

Her often-mentioned 'twinkling' wasn't just empty talk; her Inner Qi, though faint, emitted its own light.

Though the starlight was too faint to be called a proper light source, combined with Qing's exceptional night vision and the spatial awareness of her heightened senses, it was enough to illuminate her path.

As the faint starlight guided her deeper into the earth.

\textit{Sniff sniff. What's this smell?}

A subtle stench crept into her nose, making her eyebrows twitch.

Now that she thought about it, the pungent smell of coal had long disappeared, replaced by a faint but unmistakably repulsive odor.

It felt like it was seeping into her lungs, making it uncomfortable to breathe.

It was a smell Qing was all too familiar with.

A smell she had grown tired of during her first year in Wulin.

The smell of something living that had died and was now rotting.

In other words, the stench of death.