\chapter{Even In Dreams, Wishes Are Slaughtered (4)}

Shidu\footnote{屍毒; corpse poison} was, as its name suggested, a poison made from a human corpse.

However, the poison itself was not particularly toxic.

After all, humans were not creatures that harbor poison.

If a corpse was left to rot, it would simply decay; no sudden burst of poison will emerge from nowhere.

In fact, the toxicity of Corpse Poison did not come from the ingredients used to make it, but from the negative emotions of the dying person, such as their desperate desire to live, their frustration at their hopeless situation, and their feelings of injustice and pain, which were dissolved in the water.

Usually, objects imbued with such hatred were called 'cursed objects\footnote{咒物; zouwu}' and were used as ingredients for various suspicious and terrible sorceries.

Corpse Poison was one such item.

And the ones who used Corpse Poison best in Zhongyuan were the Blood Cult.

It was used in various magic spells, as an ingredient in creating demonic beasts such as ghouls and zombies, and added to evil drugs such as Jaman Dan…

Qing gritted his teeth.

\textit{Those Blood Cult bastards, what the hell are they so unhappy about?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Night was a time when emotions run high.

In Qing's hometown, it was scientifically proven that the left and right sides of the brain work differently at night, causing emotions to run high.

In any case, standing guard duty was a particularly good way to get caught up in the emotions of the night.

The surroundings were quiet, with the pleasant sound of insects chirping, and countless stars flowing across the night sky, giving the feeling that we were the only ones in the world (since we knew from experience that if you stand guard duty alone, you won't be able to sleep at all).

If you have ever stood guard duty in the military, you would have experienced the emotional turmoil of guard duty.

Those who normally spend their free time kicking a ball, singing songs, or staring at female singers on screen suddenly found themselves engaged in serious contemplation about the future, reminiscing about beautiful memories from the past, or even engaging in philosophical discussions about random topics.

This was the magic of the night.

And here, there was one person who cannot resist the magic of the night and cannot break free.

Unable to withstood the nagging of his seniors, he revealed his love story, and thanks to that, he seemed to be missing his lover, whom he had left behind in his hometown in the quiet of the night.

"The night sky seems the same here as it is in my hometown. We used to look up at it like this, and I wonder if she is looking at the same sky. If we are looking at the same sky, even though we are so far apart, it feels like we are together…"

"Hey, you're quite the poet. Once we get rid of those Zhongyuan guys, you should try writing some poetry. Who knows, you might go down in history."

"Ha ha, I don't even know how to write, how can I write poetry? Maybe it's because it's nighttime that I'm saying things I don't usually say. By the way, how about you, Brother? Your wife is in your hometown, don't you miss her?"

"No, I don't miss that nagging woman. Still, our son, I can see his face just by closing my eyes."

"Ah, your nephew. How old is he this year?"

"Let me see, one, two, three, so he's six or seven? Hmm?"

"Wow, he must be so cute."

"……"

"They say that's the cutest age. At four, they're all cute and mischievous, and at ten, they do everything they're told not to. Is that true?"

"…"

"Brother?"

The young man turned his head, looking for his senior.

But there was no one there.

It was as if no one was ever there, with no sign of life anywhere around him.

The young man waved his torch around, searching the area.

However, only the flickering shadows of the torchlight danced in the pitch-black darkness.

A chill ran down the young man's spine.

The person he was talking to disappeared in just a few steps. What on earth is going on?

Who was the person he had been talking to, and where did they go?

"Brother? Don't play around. Where are you?"

The young man's voice trembled slightly.

At that moment, in the darkness, two white hands quietly reached out from both sides of the young man's head.

Then, with a thud, one hand wrapped around his neck and the other covered his mouth.

With that, the torch fell and rolled away.

"Ugh, ugh."

The young man grabbed the arm wrapped around his neck and struggled, scratching at it.

But that was only for a moment.

The rough cloth covering his mouth filled his lungs with the stench of alcohol, and his eyes rolled back in his head.

The man collapsed to the floor.

A white hand grabbed the young man's hair.

Even in the light of the torches, she was pale and beautiful, with long, slender limbs.

Qing grabbed one of his hair strands on each side and dragged him along.

"Tsk."

\textit{The sound he makes is ridiculous.}

\textit{These beastly creatures who pile up corpses like mountains, they want to see their wives and children?}

\textit{And what else? Get rid of all Zhongyuan people?}

\textit{As expected from members of the Blood Cult.}

Qing grabbed two heads and drags them toward the mine entrance.

Passing through the unguarded entrance, inside the shadows, there were already unconscious guards lying tangled together.

Two more were thrown on top of them.

Qing looked down at the mess with a cold gaze, then turned away silently.

After Qing walked away, a moment later.

This time, a muscular, well-built man appears, lay down the unconscious men, and headed back outside.

A moment later, a man wearing a mask, but whose good looks are evident even through the mask, abandoned the unconscious people and disappeared.

Next, two women appeared, pulling a cart.

One woman should pushed and the other pulled, but they couldn't even coordinate that simple task, so they held onto the handles on either side and stood far apart, looking like they didn't get along very well. They dumped the people piled on the cart onto the ground.

People continued to pile up, and…

Finally, masked men gathered in front of the pile of people.

And finally, Qing took her place among the masked men.

"I think that's all of them."

It was Qing's group that had gathered all the miners who had been sleeping in front of the mine.

Strangely, the miners were merely unconscious, not dead.

\textit{Killing them would have been too easy.}

\textit{For me and for them.}

\textit{I never understood revenge stories in movies or comics.}

\textit{How can killing someone neatly be revenge?}

\textit{They're not going to wake up in the afterlife and beat their chests in regret, so shouldn't revenge be about making them suffer as much as possible and cry out in agony?}

So, even though it was troublesome, Qing used the medicine.

Dangga Monghonyak, Sambobae.

Monghonyak is a general term for drugs that destroy a person's consciousness.

And the Monghon-yak made by Zhongyuan' best pharmaceutical company was a well-known and notorious brand among Monghon-yak.

Rumor has it that if you inhale the smoke, you will collapse before taking three steps, and you will lose consciousness immediately without even feeling dizzy, falling down in a deep bow.

That's why it's called "three bows." Three steps and one deep bow.

\textit{Hmm, but wait.}

\textit{Why is Lan-Ah carrying this around?}

\textit{No matter how precious Lan-Ah is to the Sichuan Clan, isn't this a bit excessive as a self-defense weapon?}

Of course, Lan-Ah would laugh it off.

Even if it has side effects that can damage the lungs, it was still a poison intended to subdue rather than kill.

The great Tang family doesn't even consider such a mild poison to be poison.

"Well, shall we wake them up?"

Tang Lan-Ah slipped her hand into the baggy sleeve and rummaged around.

Then, she took out a small glass bottle, opened the lid, and sprinkled its contents into the air.

A fragrance similar to peppermint filled the interior of the mine, followed by faint moans.

Qing clapped her hands.

"Now, everyone, pay attention!"

"Huh!" 'Here.' "Who-who is it?"

"Look here. It's sparkling. And… Shh. Quiet. Be quiet. Everyone, keep your mouths shut."

Qing smiled cheerfully and wielded her Sword Aura.

There was no way to silence the people of Zhongyuan with such a simple tool.

But when they lost consciousness and woke up, they found themselves under a strange ceiling.

How could they keep their mouths shut?

To be precise, it wasn't a strange ceiling, but a familiar one, the rock ceiling of a mine.

"Damn it, what the hell is this— Ugh!"

The man, who was about to spit out a string of curses, immediately stiffened like a rock.

Of course, when a cold blade pierces your mouth, you can't even think of moving.

"Shh. Be quiet. You're not talking like a human being. I told you to be quiet. Do you want to die?"

The man shook his head desperately.

With the blade in his mouth, he shook his head from side to side, looking as if he were trembling.

"Now, anyway. Rules are rules. You have to accept the punishment. Here, take that."

Qing's conviction, or belief, or both.

If the knife penetrated the enemy's body in any way, it must not come out in the same direction.

In any case, since it entered the enemy's mouth, it must come out in a different direction.

"Ugh, aaaah!"

The man covered his face with his hands and collapsed, letting out a desperate scream from his torn cheek.

But that was only for a moment.

"Shh. I told you to be quiet!"

"Ugh! Ugh!"

The man desperately covered his mouth with his hands as the shining blade dug gently into the stone floor in front of him.

If even the man with his mouth torn apart was unable to scream, what about the other miners?

Qing nodded in satisfaction.

"Now, just in case you get any ideas, I'll show you. Here, one sparkle."

"Two sparkles."

"…Three."

Xue Iri and Peng Daesan released their Sword Force.

For reference, the original sparkle number two, Jian Buxi, was unfortunately absent as she was taking care of Ciyu.

"Alright, did you see that? Don't even think about trying to take me down together. Alright, everyone, get up. Keep your mouths shut and follow me quietly, using only your feet."

Qing said that, picked up the glass lantern, and walked backward toward the interior of the mine.

She couldn't take her eyes off the men who were rolling their eyes, trying to find a way to escape.

"Didn't you hear her? Do you want to die?"

The miners reluctantly took a step forward at Tang Lan-Ah's sharp voice and contemptuous urging.

At the same time, they exchanged glances, their eyes darting back and forth so rapidly that you could almost hear the sound.

Regardless, Qing continued walking backward without hesitation.

And the further she went, the more confusion and anxiety appeared on the miners' faces.

\textit{These bastards must have figured out where I'm going, right?}

Seeing their expressions, she couldn't help but smile.

As she watched them, she noticed that the air behind her was blocked by a dead-end rock wall.

Qing put the lantern on the ground and lifted the iron plate next to it.

However, a fierce stench filled the air. It was an unbearable, foul odor.

"Ugh." "Ugh."

Suddenly, the sound of retching filled the air.

It seems that some people were unable to hold it in and vomitted.

Regardless,

Qing finally get to the point.

"Alright, everyone knows how to climb a rope ladder, right?"