\chapter{Even In Dreams, Wishes Are Slaughtered (6)}

Qing imagined the scene below the hole.

\textit{What are they thinking?}

\textit{In the center of that mountain of gruesome corpses, surrounded by the terrible deaths they have caused, they must be racking their brains trying to decide who to save.}

\textit{It is ridiculous.}

\textit{Among the hundreds they had killed, they are picking out who's innocents to save. How could they do such a thing? How could they have no conscience?}

Qing stared down the hole for a long time.

Finally, a head cautiously poked out of the hole in the pupil.

It was the woman she had first pointed out and grabbed by the hair.

After that, heads popped up one after another.

Then, with anxious expressions, they looked around and approached the woman who had come up first, clamped their mouths shut, and glanced around.

Two, three…

There were twenty women and young men who were not yet fully grown.

"Is that it? Are you the last one?"

"Yes, yes. That's right…"

Qing swung her sword.

The sword flux gently dug into the solid rock wall, leaving a long horizontal mark, and the rope ladder that had been in the sword's trajectory disappeared deep below.

"Hmm. Twenty. You didn't ask for much. Well, this is enough."

At that moment.

Zhuge-hyun cautiously spoke up.

"Sister. Are you really going to let them go?"

"Huh? Why?"

"They are the remnants of the Blood Cult. Even if you let them go now, they will eventually join the Blood Cult's evil plot and lend their strength to them."

He wanted to kill them all.

At that, Tang Lan-Ah's eyes turned sharp as axes, and she glared fiercely.

"What? Are you telling Qing to break her promise? Is that all you have to say?"

In fact, the martial artists of Wulin were not virtuous people who strive for justice in the world.

The job of a xia (hero) was not to help good people and kill bad people.

Heroes were a race far removed from justice.

Because heroes were not justice.

The values that heroes revere were not justice, but faith, promises, and loyalty.

Sima Qian's Records of the Grand Historian said of heroes:

\begin{quote}
	Even if their actions were unjust, they were decisive and always keep their word.

They never break their promises and help others in need without thinking of themselves.
\end{quote}

In other words, they kept their word even if it meant making enemies of the whole world.

This was what Zhongyuan meant by a chivalrous man.

Among the people Qing have met recently, the one who best fit the description of a hero was none other than the Tiger-slaying Swordsman O Jik-hwan.

He negotiated with Qing to save the medicine seller TTai Ping, and the content of that negotiation was certainly something that would make people laughed and mocked him.

Chamho-do knew that the world would mock him for his proposal, yet he still tried to save Tai Ping's life.

A martial artist abandoned his pride, which he valued as much as his life, and chose loyalty.

If Qing had changed her mind and decided to kill Tai Ping, Cho Ho-do would have fought her even though he knew he would lose.

Knowing of this, Qing chose to negotiate with him using only one arm and one leg.

It was truly the behavior of a true swordsman who lived and died by his code of honor.

Furthermore, this was also the honor of martial artists.

This was why Zhuge Lixian was so careful when bringing up the subject, and why Tang Lan-Ah, who unquestioningly sided with Qing, was so angry.

If Qing claimed to be a true swordsman, she must kept her promise to spare the lives of the Blood Cult woman and children and take them to safety.

Even if that meant facing the enemies of the Blood Cult and the entire Zhongyuan.

However, we must also hear Qing's opinion on this matter.

Qing watched the standoff between Zhuge Lixian and Tang Lan-Ah for a moment.

The only unusual thing was that Peng Daesan subtly took a place behind Tang Lan-Ah.

It was a sign of his support for Tang Lan-Ah.

Zhuge Liang looked at Xue Iri with a desperate look in his eyes.

Of course, Xue Iri had no idea what was going on.

Meanwhile, Qing turned her attention to the Blood Cult members who were appealing for their innocence.

Some cowered and hunched their shoulders, some trembled in fear, and still others glared with determination, unwilling to hide their hatred.

\textit{These bastards will definitely cause trouble later.}

\textit{But, haaah.}

Qing made her decision.

"Stop it. A promise is a promise."

"But, Sister…"

"If you made a promise, you have to keep it. It's not about grand agreements or trust. If you get used to breaking promises, you'll eventually stop seeing them as promises at all."

"Ugh."

Zhuge Lixian clamped his mouth shut.

It was one of the most despicable tactics in an argument.

Using morality as a yardstick to push your own agenda.

What could he say when she was saying she would keep her promise?

The Blood Cult members looked visibly relieved.

"Now, this way. Don't try anything funny, or I'll know. I'll keep my promise, but if you break yours, then I'm not bound by any promise. So behave yourselves, you understand? It's time for us to part ways. Line up in order of seniority, in a single file, and follow me."

The Blood Cult members obediently followed Qing's orders.

"Come to think of it, Miss, you're always in the first place, right? But how can we do anything with such a timid vanguard? Now, stand up straight, like this."

Qing grabbed the shoulders of the woman standing at the front, who was cowering, and spread them out to the left and right, then kneaded her shoulders.

However, the woman's tension did not ease just because Qing suddenly became affectionate, and instead, her shoulders stiffened with tension.

"Haiyaa, why are your shoulders so stiff? I need to soften them up a bit."

"What?"

In that moment, Qing clenched her fists.

A superhuman strength that could crush stones and iron squeezed the woman's shoulders.

Qing's fingers pierced her hard shoulder blades and dug in.

The sensation filled her palms.

The crushed flesh and shattered bones mixed together like meat dough, seeping out between her fingers—

"Ah, ah…!" 

Qing clenched her teeth.

\textit{Wow, I almost fainted. It's been so long since I've felt this kind of sensation. I almost let out a moan without realizing it.}

"Aaaahhhhh!"

A sweet scream rang out right in front of her.

The woman rolled on the floor, her shoulders torn apart as if by a beast, now just lying there, her arms, which would never move again, flailing unnaturally in all directions.

The screams spread to the other Blood Cult women, and some of them immediately fell to their knees and ran away, while others rushed forward, shouting profanities.

Of course, the young man paid for his recklessness with a kick to the chest, gasping for breath as he fell to the ground.

A girl of the same age, either a friend or lover of the brave man, rushed to his side, grabbed his body, and shouted at Qing.

"Why, why! You promised to spare us!"

"No, I told you. I will keep my promises, but if the other party breaks their promise first, they are not to be trusted."

"What did we do…?"

"You're the one who did something. How dare you try to save a Blood Cult executive? You bastards think you can treat people like shit."

Qing pointed to the woman who was still writhing in pain from losing both shoulders.

She was the woman Qing chose first, the woman whose hair was grabbed, and the woman who had committed the most evil deeds among all the workers.

She wasn't just evil, she was a beast who would have scored 1,000 points if rounded up. How could such a woman be an ordinary Blood Cult woman?

The girl gasped in horror.

She was still young, so she couldn't control her emotions.

But then again, how could an ordinary Blood Cult member from a Blood Cult village control her emotions?

"Sister?"

Qing walked over and stomped on the head of the woman who had lost her shoulders.

Even as her head was crushed between the ground and Qing's foot, emitting a bestial scream unbecoming of a woman, Qing's beautiful voice pierced the ears of those around her with its clarity.

"This bitch is the one who makes the poison. It's such an important ingredient for the Blood Cult, so why would they entrust it to a bunch of ignorant fools? They would have at least one person staying there to watch over it. Right?"

Qing loosened her step slightly.

Pain can be suppressed with even greater pain, and once her head was squeezed to the point of breaking, the pain in her shoulders became bearable.

"Ugh, how…?"

For a woman who cooked meals, her evil deeds were too great.

Judging by her evil deeds, she must be a beast who committed terrible crimes.

And if she committed such terrible crimes in this mine, she must be the mastermind behind this scheme.

So, pretending to choose anyone, Qing picked her first.

But what about the trickery of that old man?

From the beginning, it was all a trick to save this one woman.

Of course, he may have had some intention of saving the other women and young men as well.

But in the end, this woman was the most important one.

"He looked at people very sparingly. What? You bastards from the Blood Cult want me to spare a woman and a child? Even a dog wouldn't believe that. You Blood Cult members don't value other people's lives, and you don't value your own lives either. I'm sure you only wanted to spare someone who is necessary for your grand plan."

Even though the accusation was only based on the invisible Evil Karma, Qing naturally came up with another excuse.

"Ah, I see! You are my Sister after all! You knew she could be dangerous, so you lulled her into a false sense of security and subdued her!"

Qing's attitude became smug.

\textit{So, Zhuge still recognizes me?}

\textit{This is the dignity of a master.}

\textit{You guys are like leeches, so I have to proceed with caution.}

\textit{Her martial arts skills didn't seem dangerous, but if she is the one who made the poison, she could have used it.}

\textit{My weak friends drink poison like water, unlike me, so they can't do this.}

\textit{Still, emotionally, I guess you guys are a little helpful.}

\textit{Other than that, well, maybe if we stick together, you might be of some use someday?}

\textit{Even dog shit was good for medicine, so maybe you weaklings will be useful someday.}

\textit{Hmm. Maybe?}

"And while you were at it, you made those Blood Cult members crawled into their own graves! As expected, you are the most brilliant at such despicable tricks! I believed in you!"

Qing, who had been raising her chin, stopped.

\textit{Huh? That's not a compliment.}

\textit{Something feels off. Am I being treated worse and worse?}

\textit{Of course, I can be as despicable as I want to such evil people, but this Zhuge guy is getting more and more ambitious.}

\textit{I need to teach him a lesson sometime.}

Qing waved her hand.

With the sound of a temple bell, the woman's legs snapped and bent in different directions.

Aaah! As another scream escaped her lips, Qing grabbed her hair with his foot and lifted her up, whispering in her ear.

"From now on, everything that happens was your fault. You shouldn't have tried to run away so clumsily. If you had fought back, you might have been able to escape, at least one or two of you."

\textit{He says he's going to give her medicine, but when you think about it, I think this iss how it was going to end anyway.}

"You, wait a minute…"

Qing threw the woman's head aside.

As the woman, whose arms and legs were crippled, collapsed, Qing drew her sword.

Why, there's a problem with that.

Are the citizens of a war-torn country really innocent?

Even if they were unaware of the reality of war due to strong control and propaganda, and accepted those lies as truth, can those who cheered for war and worked hard to support it really be considered innocent?

Weren't they members of the Blood Cult, who had been taught to hate Zhongyuan from their earliest memories?

They may be pitiful, but they were not innocent.

However.

Qing gripped the hilt of his sword tightly.

\textit{In fact, whether they are innocent or not is just an excuse.}

\textit{It's just, how should I put it?}

\textit{Everything has a priority, right?}

\textit{My friends, the idiots of our Half-Sword Double-Saber Society, our Divine Maiden Gate family, our Wulin Alliance, our Orthodox sects, in other words, us. We come first.}

\textit{The Blood Cult are the ones who dream of destroying Zhongyuan, and my loved ones belong to Zhongyuan.}

\textit{I don't need any other reason.}

\textit{Still, if there is any consolation, it is that these Blood Cult bastards truly deserve to die.}

\textit{They are evil people who can be killed without hesitation.}

\textit{I'm glad they are people who can be killed.}

\textit{As Zhuge said, even if I kill you, my family and my people will understand and support me.}

Qing smiled wryly.
