\chapter{Even In Dreams, Wishes Are Slaughtered (5)}

Qing pretended to be excited.

"Wow, a secret passage! How can I resist? Where does it lead to? Come on, everyone, a man must dig into a hole when he sees one. Come on, one by one, who is the manly man who will be the first to enter this unknown passage?"

The miners all turned their heads.

Some lowered their eyes, while others looked around nervously, avoiding Qing's gaze.

Qing raised her finger and waved it around.

"No volunteers? Come on, let's choose one. Try to guess! Ta-da, you're the winner."

"Me? I'm clearly a woman, I'm not a man…"

"Come on, women can do anything! In fact, important tasks are usually done by women. Aren't all men born from women? So don't be shy. Come on."

Chung tapped the entrance of the vertical cave twice with the tip of her sword.

The woman she pointed at flinched and shrugged her shoulders.

"Don't worry. We're all going in together, so what could we possibly fail to accomplish?"

Qing took a slight step forward.

Qing shifted her center of gravity forward and simultaneously pushed off the ground with her toes.

It took only a blink of an eye to leap across the distance.

With a whoosh, the wind blew past, and the woman's horrified expression came within inches of his face. At that moment, Qing reached out and grabbed her hair.

She grabbed her hair violently, and the woman-

"Heeek…! Kyaa! Let go, you… Kyaa!"

Screaming, the woman grabbed Qing's arm and scratched her, causing a commotion.

It was a futile resistance.

How could she scratched away the hand coated with invincible Demonic Arts with her fingernails when even swords couldn't hurt it?

"Let go, let go, hee-hee, Sir, let go, please let go."

"Wow, you don't know what to do because it feels so good. Well, I guess that's natural. After all, exploring a cave is a journey into an uncharted new world, an opportunity to plant the first flag of mankind wherever you go."

"Hee-ik, please, I'm sorry, I'm sorry, so please!"

The woman, whose hair was grabbed, rubbed her arms together like a fly and repeatedly cried out that she was sorry.

But Qing pretended not to hear her.

That was the moment.

"Wait a minute!"

\textit{Isn't 'wait a minute' informal?}

\textit{But what can you do when you're in a hurry? I'm a generous person, so I'll understand.}

Qing turned her head and saw a middle-aged man, who would be called an 'uncle' in her hometown, stared at her with trembling eyes from among the workers.

"What is it?"

"Sir, that child is innocent. She is just a child who cooked and did laundry. Please, have mercy on her."

The elderly man's words were polite, but only in form.

His distorted face and trembling voice betrayed his sense of injustice, anger, and humiliation.

However, to Qing, it was rather welcome.

"She's innocent? Because she iss just cooking and doing laundry?"

"My lord, that child doesn't even know what's going on here. She just volunteered because they needed help at the mine, but she's never even set foot in the mine before."

"Elder!" "You!" "Shut your mouth!"

Before the elder could finished his sentence, cries erupted from all around.

Some cries were filled with concern, while others were filled with anger.

It was only natural.

Didn't the elder say so himself?

This woman was innocent and has no idea what was going on here.

In other words, it was an admission that some of the people here were not innocent and already knew what was going on.

Furthermore.

There were more than a few people who had been watching the situation and were now finally speaking up to silence the old man.

Even if the worst came to the worst, they would hide their true identities as members of the Blood Cult and pretended that they were just miners who had come to work, and either die while deceiving everyone until the end, or appeal for their innocence and seek to save their lives.

Whether they were coerced, brainwashed, or agreed among themselves, it meant that they had already come to an agreement.

So, the elder's proposal was this.

"You'll tell us everything you know, and you'll point out the ones who should be killed, so please spare the innocent ones?"

"!!" "—-!!" "!!!"

At that, people here and there began to shout, "Kill him! He's a traitor! What about the cause?"

Of course—

"Kyaaah!" "Aaah!"

The commotion was quickly suppressed by a demonstration of nuclear honey bombs.

The sight of the laborers clutching their heads and writhing on the ground in agony made everyone swallowed hard and fell silent.

"You're interrupting the adults' conversation. You're just showing your lack of manners. Come on, old man."

"Sir, there are innocent people here who have never even held a sword or a club, let alone practiced martial arts. We have already seen blood, but I beg you to show mercy to the young ones who don't know any better and the women who know nothing."

It was a resolute decision.

Rather than keeping the secret until the end and being killed, he would rather save the women and children (although they were more like teenagers than children).

Qing rubbed the chin of her mask.

She pretended to consider the proposal, but what she was actually thinking was, 'This silk is uselessly good, and it feels nice and soft…'

After enjoying the softness of the silk for a while, Qing finally uttered a single word.

"Talk."

"First, please let the women and children go, and then I will tell you everything."

"Once I make a promise, I always keep it, no matter what. Trust me."

"But…"

"If I let them go? Will they be safe outside? Do you think there are only five of us here? Or do you want  one of us to lead them?"

The old man's expression clouded over.

As Qing said, if they knew their identities, would they have come with only five people? Come to think of it, would only five people be enough to subdue and gather all these people?

There were three Transcendent Realm masters there.

Transcendent Realm masters were the most powerful fighters in any sect, so they would have brought at least one combat unit with them.

But how could anyone imagine that they would have come with just these people?

"And what if we don't believe you? Honestly, do we really need to know what you Blood Cult guys did? We can just kill you all and be done with it."

This was not a threat, but her true feelings.

It was obvious that even the best of them would be second-rate at best, having never learned any martial arts.

There was no benefit to bring in guys who knew how to fight and then make them work in the mines.

So even if they spilled everything they knew, it wouldn't be much useful information.

Besides, there was no guarantee that what they said would be the truth.

Then why Qing bothered talking to them?

Just in case.

"…I'll tell you everything. We are…"

The middle-aged man calmly began to tell his story.

They were simple laborers mobilized from the Blood Cult villages.

They were just ordinary Blood Cult members who did not belong to the organizational structure of the Blood Cult executives led by the so-called 'high-ranking members'.

They just came to this mine as ordered by their superiors, mined coal as usual, and occasionally killed and threw into the pit any Zhongyuan people who came in.

"What about the people who made the poison? Surely there must have been people who checked to see if it is ready?"

"Well, the executives would never bother to visit lowly people like us."

"What? What do you even know?"

As expected.

The information was useless.

\textit{I thought that none of them are skilled martial artists, and that they are just a bunch of sloppy guys who stood guard without any system.}

They were just people mobilized from Blood Cult villages who didn't belong to the main branch of the Blood Cult.

There wasn't a single piece of useful information.

It seemed like they didn't even know that piling up corpses was a method of manufacturing poison.

Which branch of the Blood Cult was responsible for manufacturing the poison, and how many executives were assigned to the task?

Or the whereabouts of the medicine, and whether there were other mines like this one where they lure people with medicine.

Qing let out a deep sigh.

Perhaps because they were nameless scoundrels of the Blood Cult, their tricks were so shallow.

The reason was that the men who were angry at the elderly man's intention to surrender and were making a lot of noise earlier, or to put it bluntly, the fanatics of the Blood Cult, were now quietly keeping their mouths shut.

Why?

At first, they were angry and noisy because they thought the elderly man might actually speak up and revealed something they wanted to hide.

And now, they know that the information the elder was spilling has no substance.

They've realized that he had no intention of revealing any real information, so they're keeping their mouths shut and not interfering anymore.

"Ugh. We wasted our time. Come on, it's getting late. One by one, climb down the ladder."

"Me, sir! The promise…"

"Hey, you have to listen to people until they finish speaking. Get down first. Then pick the innocent persons you mentioned and send them up."

"But—"

"Enough. Do you think the women know nothing because they're busy cooking and doing laundry? From now on, they'll know. Even if I spare their lives, they must come down and see with their own eyes what you've been doing in here, what kind of people these children are who were fed and clothed by them."

The older man tried to protest, but in the end, he just shook his head.

He could hear the murderous intent and clear anger in Qing's voice.

It was a stern warning to listen when she spoke, and a final warning that she would not say it again.

Qing clapped her hands to get everyone's attention.

"Now, I will tell you what will happen to you. Once everyone who was to be spared has come up, we will remove the rope ladder and set fire to the mine."

Once the coal seam catched fire, there would be no way to extinguish it with manpower.

However, once the mine collapsed from the heat, oxygen would not be able to reach it, and the fire would eventually extinguish itself.

However, even amid the chaos, the chamber deep underground woulld remain safe.

The heat rises upward, so it won't reach the natural caves deep underground. Therefore, even if the mine collapsed, the poison factory below would remain intact.

So even if the mine collapsed, the Blood Cult members would be safe.

However, they won't be able to get out.

"I wonder how long you can hold out. The water there looks pretty deep, and you know that rock water is usually pretty fresh, right? You will have water to drink and air to breathe, so let's hold out with as much hope as you can. Who knows? Maybe your Blood Cult bastards will dig through the collapsed mine and rescue you."

It was a terrifying plan to bury them alive.

\textit{There's air and water, and since it's underground, the temperature isn't too bad. If you can find food, you can survive, right?}

\textit{What can you eat?}

\textit{There are a lot of rotten corpses, right?}

\textit{No, they're already poisoned, so maybe they'll draw lots and eat the lucky one?}

\textit{Wow, just thinking about it makes my heart race.}

\textit{It's a fitting end for scum like them.}

The Blood Cult members' eyes trembled.

However, even knowing the terrible end that awaits them, they had no choice but to quietly went underground.

Because those who can be saved must be saved.

Even among these people, there must be someone they want to save.

"Now, old man. Who should go first? Those who are to be saved go first, and those who are to die go later. Now, let the underground exploration begin."

The middle-aged man turned his head toward her.

The woman whose hair was still grabbed by Qing was the first to go. The woman who caught his gaze quietly sobs and slowly lowers her body into the hole in the floor of the mine.

Qing watched for a moment until the woman disappeared, then spoke again.

"Now, next. By the way, we have to hurry. I don't know how many people can fit on the rope ladder, but if too many people hang on it, it could break."

One by one, the mine workers climbed the rope ladder and disappeared into the hole below.

From midway down, there were screams of "Kyaaah!" and "Kkwaah!"

Then, 'Uweek!' and 'Gek!' sounds of vomit erupting from deep within their bodies began to rose from the depths of the underground.

Even the most hardened members of the Blood Cult would be a million times more impressed.

A mountain of human corpses, various corpses kindly showing the process of human decay, neatly stacked like specimens.

\textit{Hmm, it would be interesting if the rope ladder broke at this point.}

\textit{The rest would have no choice but to jump.}

\textit{The so-called 'innocents' who are supposed to come out later would also have no way to return. Ah, there is no way to keep the promise, so I had no choice.}

Unfortunately, however, the rope ladder was very sturdy and of high quality.

"The promise…"

"Don't worry, I'll keep my promise. You're the last one, right? Once everyone are down, send them up right away. But don't get greedy and try to save even one more person, or I might change my mind. Do you understand?"

"…Yes, I understand."

Finally, the elderly man disappeared.

Now the mine shaft was completely empty.

The blue eyes staring at the gaping black hole in the floor were now tinged with an eerie, otherworldly hue, as if the world itself had turned into a nightmare.