\chapter{Even In Dreams, Wishes Are Slaughtered (3)}

A foul odor of decaying corpses wafted through the mine.

It was a faint, subtle scent, barely noticeable unless one had a keen sense of smell.

\textit{Perhaps an animal carcass had rotted away.}

\textit{Or maybe a bear hibernating for the winter had been discovered… No, that doesn't make sense…}

This isn't a cave; it's a mine, a space dug by humans. There's no way an animal would hibernate here, especially since it's warm even in winter.

Moreover, even if that were the case, why would anyone leave an animal's corpse to rot like that?

But in such a closed, unventilated underground space, they wouldn't just leave the stench—the most foul smell of all—to linger.

Or maybe there was an accident.

The mine shaft collapsed, and they had no choice but to leave the body beyond to rot.

Perhaps the station's curse originated there.

Why do such clichéd stories often appear in horror tales set in mines?

Miners trapped under collapsed tunnels and rescue plans that never materialize for some reason.

Digging to rescue them could cause the entire mine to collapse, or perhaps a heartless merchant decided that it would be cheaper to clean up the mess than to rescue them, or maybe they just wanted to quietly sweep it under the rug…

If that's the case, then even now, the injured people buried in the mine are waiting helplessly for someone to come and save them.

Qing closed her eyes for a moment and listened intently.

However, even her keen ears cannot hear a sound, only the loud sound of her own breathing echoing inside her body.

Suddenly, she realized that the world is too quiet.

But then she realized that it has always been this quiet.

And it is too dark.

The starlight of Inner Qi is nothing more than a cold blade for murder, so it is only natural that fierce evil cannot shine brightly.

Therefore, the surroundings were infinitely dark.

The world was nothing more than faint shades of light and dark, like a sketch drawn with vague lines.

Qing wandered in the silent darkness.

Chasing after the unpleasant aftertaste that barely touches her nose, she headed toward the depths of the earth, not even knowing which direction to go.

She continued like this for a while.

How much time has passed?

Finally, a rock wall blocked Qing's path.

The end of the tunnel.

An hour? An hour and a half?

Or maybe just a few minutes.

In this dimly lit space, where not even the slightest sound of nature can be heard, time was an agonizing unknown.

Of course, if you deg straight down into the ground, that's a tunnel, not a mine.

Given the nature of the mine shaft, which branches out like an ant hill (though not as complex), she must had reached the end of one of the passages.

\textit{But the smell is coming from here…}

And then, thud.

Suddenly, Qing's toes tapped something.

Due to her physical characteristics, the area under Qing's feet was a vulnerable blind spot that she could not see.

Even so, she had never tripped over anything before, because Awakened Sense Divine Art gave her omnidirectional vision and spatial awareness, allowing her to read the space beneath her feet.

Therefore, if Qing tripped over something while walking, it meant that she had deliberately touched it, not that she had made a careless mistake.

Qing's toes tapped the floor again.

This time, a soft tapping sound echoed, as if someone is gently striking a metal plate.

It was a metal plate embedded in the mine floor.

Pieces of cloth were wedged into each corner of the rectangular plate.

It appeared to be sealed tightly, with no gaps between the plate and the ground.

Inside the mask, Qing's expression hardened.

A certain premonition, a feeling of foreboding that gripped her heart, suddenly rose up inside her.

\textit{No, that can't be.}

\textit{I haven't had any feelings about it so far.}

\textit{I thought it was an opportunity for slaughter, but it wasn't. It's been a long journey from the medicine man to here.}

Qing tried to think positively.

\textit{Ah, could it be? A drain?}

\textit{Hmm, a drain in the middle of a mine doesn't make sense.}

\textit{Well, they probably didn't seal it up this carefully.}

\textit{Ah, no way. It's not a toilet, is it?}

\textit{Come to think of it, miners have to take care of their bodily functions too, and they can't just go outside every time.}

Sling, the sword is drawn.

The sword pierces the piece of cloth blocking the gap between the iron plate and the ground.

\textit{In this suspicious situation, I have no idea what the cloth was used for, but in the worst case, it could be reused from the cleanup crew.}

\textit{So I can't touch it with my hands.}

But stabbing that suspicious cloth with a sword didn't look normal either.

Some might even foam at the mouth, wondering what kind of swordsman she is.

But Qing had always used weapons without hesitation.

And after all, a sword was a tool meant to pierce an enemy's body, so wasn't it more effective the dirtier it is?

Qing carefully pulled the sword back.

Pulling the cloth bundle out from under the thick iron plate with the sword blade seemed simple, but it was actually a feat that defies logic.

However, thanks to her sword training under Tian Yoxue, Qing handled the blade as if it were her own fingers. Finally, the cloth, which had been pulled out and stretched, is suddenly yanked out and fell to the ground.

At the same time, a foul odor wafted toward her.

Qing found the source of the smell.

She lifted the thick iron plate.

It weighed over 100 kilograms, but Qing lifted it as if it were a straw mat.

Then, a vertical hole appeared, revealing a lifeline.

"Ugh."

The foul odor that suddenly filled her lungs was so intense that even the usually composed Qing had to force herself to swallow the rising nausea.

Judging by its appearance, it was not a hole dug by humans but a natural cave that had been buried underground.

It was about five zhang deep.

The rope ladder hanging from the edge of the hole had metal hooks and was shiny and worn from use.

Furthermore.

At a depth of about five zhang, the bottom could be seen.

Even with the light of enhanced qi, it was pitch black, and only shadows could be seen.

At that moment, the distant scene below became clearly visible, indicating that a light source was illuminating the space.

And Qing knew exactly what that light source was.

In the highest guest room of the Seolga Sanghoe, a room with a grand name like "Supreme Being," therehad been a subtle, light green night light installed.

No matter how she looked at it, she couldn't understand the mystery of Zhongyuan. It was the subtle green color unique to Yamei.

Qing held onto the rope ladder and headed down.

The airflow rising from the bottom of the vertical cave is filled with a foul odor, so intense that it makes it difficult to breathe and causes a headache.

And at the bottom of the vertical cave.

A wide natural opening reveals itself.

And the bodies of people piled up like mountains.

Qing hung from a rope ladder dangling from a hole in the ceiling, gazing down at the horrific scene below with eyes tinged with an ominous color.

Normally, when a person died and was buried in the ground, they naturally decomposed into nutrients for insects and plants, following the laws of nature.

However, when a person died and did not come into contact with nature, that is when the horrors of the afterlife began.

How much more so in a cave where not even a handful of soil could be found, and where even the common insects found in rock were rare due to the harsh environment of the mine.

There was not just one mountain of corpses, but many.

One pile was nearly reduced to white bones, with flesh and internal organs melted away, forming a thick, pitch-black pool of decaying fluid on the ground, indicating that considerable time had passed.

Another pile had swollen grotesquely, forming a massive mound of flesh, resembling the early stages of decomposition, relatively intact.

It was akin to a mass grave.

Every time the families of the sick, who had sold their bodies, arrived together, the bodies were slaughtered en masse and piled into towers.

Suddenly, the face of a coal miner who had smiled kindly and replied, 'This is enough to make a miner', flashed through her mind.

\textit{How foolish—just because they were in a mine, what guarantee was there that they were miners?}

\textit{They must have been part of the same group from the start.}

\textit{With hundreds, perhaps even thousands of corpses piled deep within the mine, it was impossible for the mine workers not to know about them.}

\textit{If they had been killed outside, they would have carried the bodies here and thrown them into the underground shaft.}

\textit{Even if they had tricked them into coming here and pushed them into the hole, how could they not know that hundreds of people had entered and never returned?}

\textit{Why, why did they do this?}

Qing's eyes narrowed.

\textit{It could be some kind of ritual or sorcery.}

\textit{Like the lair of the Blood Cult in the former Qinghae region.}

\textit{Or, or, or why?}

Unless you're a sorcery expert like Danlun Zhenren, it's hard to even guess why these people were quietly rotting away in a deep, unknown cave.

So, Qing didn't bother digging up the piles of bodies or looking around.

Instead, she quietly climbed up the rope ladder.

Because if she didn't know something, she could just ask.

Shee would ask the one who knew the answer, the one responsible for this tragedy.

And she would held him accountable for his crimes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The reason why the others followed Qing to the foot of the mountain near the mine entrance was not to help her, but to keep an eye on her.

They were worried she might caused trouble and then left on her own.

Everyone already understood her motives.

She didn't want to drag her friends into any kind of danger, so this was her way of showing consideration and affection.

The problem was that such one-sided consideration felt incredibly hurtful and resentful.

'As the esteemed master of Hwa-gyeong, it's more convenient for me to act alone, and having to worry about you would be an inconvenience. It would even hinder the great master's abilities.'

If you heard that, you'd feel guilty and wronged.

But it's not wrong, is it?

Honestly, if you were even as skilled as Hwa-kyung, I would have trusted you completely.

And do you know how dangerous and violent the Jianghu is?

Now that Hyun-gyeong has appeared, threatening to kill me with a sword, if I were to encounter an opponent I couldn't even handle myself and had to worry about you, what if you were seriously injured?

From that day on, a pathetic wanderer would appear in Zhongyuan, ashamed to look up at the sky and living a life of regret, just like Kim Ssanggat, or rather, Seomoon Ssanggat.

How could the others not chased after Qing?

Qing was very nosy when it comes to other people's problems, meddling in everything like the vast sea.  She'd say 'I can take care of myself, so please leave me alone'.

That's why, when they heard Qing's claims about Jeongga's suspicious behavior, it sounded plausible, but that was all.

They didn't take it seriously at first.

In this vast Zhongyuan, there were many swindlers, and even if someone was suspicious, there were many other ways to kidnap someone.

They could use the mine as an excuse to sold people into slavery, or they could use them for activities prohibited by national law, such as growing drugs or smuggling salt.

Or that's what they thought.

The look in Qing's eyes when she returned from her infiltration mission was not normal.

On top of that, there was a terrible smell on his clothes.

Unlike in Qing's hometown, it was not uncommon for people in Zhongyuan to encounter such smells.

It was an era when it was not unusual to find dead bodies abandoned on the side of the road.

Even if that weren't the case, the smell of death also emanated from animal carcasses, and Zhongyuan is a wild land where large animals roam in the mountains behind the village.

And then, stories that we far more gruesome and cruel than expected begin to emerge.

Human corpses were piled up like mountains.

They were hidden deep within the mine, separated by rank and piled up separately.

"We should inform the Alliance first. They committed such atrocities in secret, and you mentioned that a Yamingju was embedded underground. Such construction work requires both manpower and funds. Who else but the Blood Cult could have done this?"

Zhuge Lixian trailed off, but most of the others understood what he was saying.

The Blood Cult.

Who else but the Blood Cult would commit such atrocities?

Just then, Tang Lan-Ah, who had been deep in thought, asked Qing a question.

"By the way, Qing'er, what about the environment of that place? Was it damp?"

"Well, it's a cave, so…"

"Then, the corpses, you said they were piled up, right? Were they piled in a hollow floor, or were bricks or something like that stacked around them? Anyway, weren't the let the corpse water collected?"

'Corpse water' referred to the liquid that seeped out of decomposing corpses.

Qing slightly furrowed his brow.

\textit{They hadn't surrounded it with bricks, but thinking about it, the rotten water had pooled thickly beneath the pile of corpses.}

\textit{Well, it was only natural that the corpse fluid would seep out of the bodies.}

Tang Lan-Ah frowned seriously.

"That sounds like they were trying to make Corpse Poison."