\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (14)}

I never imagined that eight masters of Hwagyeong would show up.

That's truly incredible power!

If they had the power to confidently step through an open door without any suspicion, wouldn't they be arrogant enough to destroy any traps they had prepared?

But that arrogance will kill you.

When Manra Daehyeolmyeolcheonjin was activated, they were all dead.

In the most terrifying illusion, the living were terrified and cry out for help like a child, and then collapse from exhaustion.

However, Hyeon-gyeong-in herself and her followers were not affected by the Manra Daehyeolmyeocheonjin.

All you have to do was harvest the lives of those idiots who were too scared to do anything.

How easy was this?

The Giant Pagoda Emperor was satisfied.

I have never been this satisfied.

It was such a thrilling feeling that it was as if I had been living for this moment.

"Kuuuuuuu, your sin of daring to invade the sacred mountain with your lowly and filthy bodies cannot be repaid even by death. However, I, who follow the will of the merciful Buddha, will generously grant you your lives. Gaejin!"

And the sun turns blood red.

A huge bloody sun.

A size that cannot be seen with one eye.

It was a giant star that covered half the sky.

Countless cracks appear in that ugly face.

Not cracks, but eyelids.

Millions of eyes open and scan the earth.

Then darkness falls on the earth.

The world will soon change.

The universe that was superimposed in the blink of an eye.

The earth was filled with holes, the smell of raw meat and blood, and the shape of half-rotten flesh changes.

The sound of countless blood vessels stretching out and thumping.

The temples of the mountain have lost their original form and were now made of bones and internal organs.

On the constantly creaking wall, countless parasites wave their white and yellow tentacles.

In an instant, dozens and hundreds of arms rise from the ground and envelop the living.

Countless blisters swelled, burst, and popped again, and pus bubbled and flowed out thickly from the arms.

"Wh, what, let go, let go!" "Eek, Primordial God!" "Eww!" "Save me!"

In an instant, the son-in-law was in chaos.

Kunlun's warriors start a fight, waving their arms and legs to shake them off, and swinging their swords to try to cut off their arms.

But the fist and the sword simply pass through the air, so there was no feeling of being caught, as if cutting through an empty illusion.

But it was never welcome.

A wet hand grabs the torso of the living.

The arms covered in blood and pus that rose endlessly continued to grab and pull, and the living were half buried in the pulsating flesh of the earth, and only a shrill scream could be heard.

Manra Daehyeolmyeolcheonjin.

It was a genie that borrows the power of the most impure star and spreads its unholy illusions over the earth.

It was impossible for the living to dare to confront the stars.

Just cry in fear until you die of exhaustion.

It was a terrible, desperate death, with one screaming endlessly until one's throat was hoarse and blood was running down it.

So Qing-

Huh? Isn't that a friendless star?

What was it? Why does it appear so naturally?

Qing frowns and looks up at the sky.

Then, some of the millions of eyes meet the blue one, and their pupils dilate greatly, taking on that characteristic colorless hue.

What, why were you here, it seems.

And then he'll pretend not to see and look away.

"No, what was it?"

Qing was speechless.

Come to think of it, isn't this the same scenery I've seen countless times at the entrance to the horse riding world?

Of course, the entrance to the devil's gate that Qing experienced was decorated with a special decoration for the evil spirit, making it a much more horrifying sight than others.

That was when.

Swish, a boneless arm extends its evil hand towards Qing.

Then snap.

"What, where?"

The arm with the pus on it waves its palm back and forth in confusion.

What were you touching me for? Am I mistaken? It seems like that.

Soon, he rushed towards Qing again, stretching out his limp arms, and then, bang!!

Should I call it a slap or a big hand bump?

But since the strength of the blue was not ordinary, either way, it would have been a huge blow that would have broken the wrist.

The fleshy arm falls off in a big way.

And then, wouldn't the flesh that touched the ground be dragged away by some unknown mechanism and hurriedly moved away?

What the heck, it's running away?

I was blinking my eyes wondering what on earth was going on when Qing chased after me and pulled me out.

"Eek, shi, no, squeak……!"

Qing's head jerked up at the familiar groan.

A familiar back of the head, pinned to the floor, held by countless hands.

"Oh, come here!"

Qing, startled, runs towards Xue-i and grabs her pus-filled hands.

But it has no effect at all.

After all, the truth was not a real thing, but an illusion felt by the mind.

Suddenly, Qing remembered a strategy he had encountered before.

What did you do then?

Oh, right.

Qing-i gently slapped Xue-i-ri's cheek.

Sorry, Gunyeong. I don't mean any ill will.

That brings a little light back to Xue-i-ri's wavering eyes.

"Miss Ximen?"

"Come on, come to your senses."

"I can't move-"

Qing grabbed the arm that was sticking out of the fleshy ground and pulled it out.

It's so painful to cut it off, and blood and pus were flowing out of the cross-section, but I can't see any bones. What was this?

As I was pulling it out, Xue-i-ri raised her body and removed the rest that was stuck to me.

The hands that rise up again try to grab Xue-i-ri, but unlike before when they didn't work, they freeze in front of Xue-i-ri's head and break.

Of course, Qing's method, the slap of love, could not escape Jin's influence.

The perception that it was simply untouchable was overturned by Qing.

"Ugh……!" "Sniff, whimper, let me go……." "Gwaaak! Eww! Eww!"

Oh my goodness. These things.

Qing's eyes narrow.

It was a mountain gasping for breath, a weeping white plume, and a monster screaming so loud it was ear-piercing.

Oh my, my fate. How can I trust these kids and entrust them with my back?

Likewise, I want to slap your cheek a little to bring you back to your senses, with a love whip.

Wouldn't someone rush in front of you and grab you by the shoulders?

"Disciple! Are you okay?"

Ximen Surin's expression was extremely urgent.

"Yes, I'm fine. Are you okay, Master?"

"Once you reach the level of wisdom, you will be able to discern even the lies of the world. Such tricks won't work."

Ximen Surin shows a look of great relief upon seeing Qing's 'expression'.

That was when.

"You fooled me! How dare you! Two Hyeon-gyeongs! How dare you! You, you, vile! You vile bastards! How could two Hyeon-gyeongs come and do such a cowardly trick, and still call yourself a political faction!!"

A loud, angry voice was heard.

When Qing peeks over Ximen Surin's shoulder, he sees the Sword King swinging his sword and the Giant Pagoda Emperor retreating, repeatedly striking back.

The best moment of Emperor Geotap's life was shorter than expected.

Even when the formation was unfolded and the goons rushed in with a shout of "Hey, you bastard!", the feeling was still good.

Did you overcome illusions by training yourself as a Buddhist monk who serves false Buddhas?

Come, I'll blow that brains out in one go!

And so, as the Giant Pagoda Emperor stretched out his head, a huge, bloody handprint as long as a chapter rose up like a barrier and shot out.

Then the monk stepped sideways and extended his fist, and bang!

The blood seal of the current was shattered in an instant, and the body of the Heavenly Tower Emperor was pushed away.

The Giant Pagoda Emperor opens his eyes wide.

"Baekboshin Kwon! You bastard!"

It was the moment when the greatest moment of Emperor Geotap's life was shattered in one blow.

"You were a villain of the Blood Cult. The Blood Thunder Cult has joined hands with the Blood Cult. Huh, Namu Amitabha Buddha……."

"Huh. It's too late. I've activated the Extinction Circle, so if I just hold on and hang on—"

At that moment, the face of the Giant Pagoda Emperor distorts, and he swings the stone staff horizontally with both hands.

Zeng!

A massive blade, more than three long, splits the sky in half and was embedded in the center of the stone wall.

The Giant Pagoda Emperor digs into the ground up to his ankles.

The poor flesh was torn to pieces, but rotten blood spurts out and spreads in all directions.

"Huh, a blood sect? Senior, didn't you say something like that? Isn't this the Manra Daehyeolmyeolcheonjin? I've only heard about it, but seeing it in person was much, um, more horrifying."

A man appears, calmly swinging his sword.

The Giant Pagoda Emperor was crying.

"What! Are you Hyeon-gyeong too?"

"It's called Nan-Gong-daero. People call him the Sword King as they please, but it's embarrassing to call someone like that when you're talking about your senior."

Nan-Gong Daero, who secretly showed off his pride in his nickname, said that.

And actually, I think that if he was the Sword King, then the nickname of the best sword in the world would be appropriate.

If your senior godmother becomes the Sword Emperor, then there was no problem with you becoming the Sword King, right?

The Giant Pagoda Emperor has this!

"You fooled me! How dare you! Two Hyeon-gyeongs! How dare you! You, you, vile! You vile bastards! How could two Hyeon-gyeongs come and do such a cowardly trick, and still call yourself a political faction!!"

"Even when hunting rabbits, a tiger does its best. For a member of the Blood Sect, even extreme measures were not a problem."

"Ugh, damn it! Hit me!"

Tink, tink, tink!

The Giant Pagoda Emperor shakes the bell noisily.

Wunue's expression hardens as he recognizes Bangul.

"Vampires! You guys were truly……!"

"Hahaha!" "Food! Food! Fresh food!" "I'm hungry! I'm hungry!" "Yay! It's ancestral rite food!"

Bang bang bang! The sound of a door opening, or rather, a door being smashed, resonates repeatedly, and a swarm of maddening screams approaches.

"Ugh, you vile bastards! I won't forget you! Here's some food! Chew up all the Kunlun bastards!"

Wouldn't the Giant Heavenly Emperor shout like that and slowly back away?

"Senior, please take care of the Kunlun children. I will take care of them."

"Be careful, I'm one step ahead of you."

"Isn't it just a matter of holding on?"

That was the moment.

The Giant Pagoda Emperor, who had been watching the situation, flies away.

Well, Emperor Geotap was in the middle of the Hyeon-gyeong era.

Even with just one Ambassador Wunue, there's no chance of winning, so if the Sword King joins in, wouldn't it be no different from suicide?

The Sword King runs after him.

The reason why Wunue did not pursue was simple.

"Go away!!!"

The famous Shaolin Lion's Tale spreads widely.

The spirit of the Pasa Hyeonjeong, the method of Jeongjong to break down falsehood and reveal what was right.

A huge force of wind swept through the room, and the fleshy arms, dripping with blood and pus, were immediately turned into dust and scattered.

The Kunlun warriors who were screaming and causing a fight suddenly stopped moving.

"Huh?" "I was being dragged in."

"Wake up! Listen to the Dharma, break free from your false illusions, and quickly leave the Dharma camp, for the demons were coming."

Suddenly, a thought flashed through Wunue's mind.

If one does not realize the subtlety, the living cannot escape from the truth.

So then, where on earth have all the Lamas of the Blood Thunder Demon Temple gone?

Wunue looks at the main gate of Hyeolryeumsa Temple.

A huge door that was suddenly closed.

It was open when they came in, so if someone had closed it from the outside, wouldn't the rest of the monks be waiting outside for any escapees?

"The monster was coming! Everyone, get your checkups!"

Wunue shouts and chants the Maha Prajna Paramita and the Diamond Sutra loudly as he heads towards the Kunlun School warriors.

Because, in the midst of the formation, the continual recitation of the Lion's Wrath, which has taken the form of an illegal act, was necessary to maintain the sanity of the Kunlun warriors.

Meanwhile, Ximen Surin locks eyes with Qing.

"I have a task for you, my disciple. The Manra Daehyeolmyeolcheonjin formation relies on the power of the evil spirits. I was worried that you would be more affected, but my worries were unfounded. Since you were not affected, you must destroy the formation."

"What should I do as a disciple?"

"There will be a sacrifice offered to the evil spirit at the center of the truth. Find it and kill it. I need to help Nan-Gong-ga, and Wunue will be preoccupied with reciting the Lion's Wrath."

The reason why Ximen Surin was different was kept hidden.

Because I already heard from my disciple's ramblings that he wouldn't be attacked by demons.

It would be much safer to go out alone now than to guard Kunlun's unmanned forces.

"Then, please."

"Yes, leave it to me!"

Ximen Surin smiled faintly, and the sword was pulled out on its own, flew up, spun around, and landed in a low trajectory at his feet.

Ximen Surin, who was lightly climbing on top of it, quickly slid down and chased after the Sword King.