\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (18)}

He was a monk of some age, so he must be paying his age.

Runlin scolds his disciples.

"[Remember our people, oppressed even at this very moment by the oppression of Zhongyuan bastards! Are we going to sit back and do nothing?]"

To Qing who was watching and listening from all directions at that moment, it was an absurd sound.

What the heck? You annihilated your own people, who were not oppressed. Where on earth do you think they are?

The cause was originally this dangerous.

Because when you were obsessed with a cause, you become blind and deaf, unable to see or hear the world, and you consider all your actions to be righteous and great.

So, Qing's impression was simple.

Well, those guys I'm going to kill.

"[Master?]"

"[Now, wake up. Something was terribly wrong. Either the Emperor was in danger, or the formation has gone out of control. This was why we must come to our senses.]"

"[Ha, but didn't the Emperor say that it was a annihilation zone without a living being? What can we do—]"

"Shut up! Where was the formation without a living being? That's how difficult it is, that's what I meant. Everyone, wake up and get up! Are you just going to sit there waiting for rescue, which may come at any moment?!"

"[But, where were you going……!]"

Someone protests in a choked, wet voice.

It's an empty space where nothing exists.

Wouldn't a vast horizon stretch out in all directions, without a single speck of dust, except for the mercury-like liquid that rose sharply?

Okay, mate!

Oh, Qing was a little impressed by the slap that was given so harshly.

Runlin scolds sternly.

"[Weak words! With such a mindset, how can you possibly achieve greatness and guide our people to paradise? If we don't go to hell, who will?]"

The lamas of Blood Thunder Temple stand in line, their expressions of fear evident, but they look at each other and overcome.

"[Everyone, tie each other's clothes tightly and hold onto them with your hands! The direction of the formation was different from reality, so if you make a mistake, you'll scatter!"

Thus, the lamas of the Blood Thunder Temple tie the hems of each other's clothes together and form a long line.

Qing thinks about it for a moment.

It seems like Captain Ttaengjung has quite a bit of guts.

It's bothering me, should I put it aside for a moment?

Or, um. Yeah, no.

Qing smiles strangely.

To destroy the villain, Qing's brain, which he usually doesn't use much, was working at full power.

The formation seemed to shake violently, then began to boil and sway, and the hollow circular formation twisted and undulated like a snake, creating chaos.

It's not a grand gesture.

It was a phenomenon that appeared because I was in a state where I was just moving my arms and legs.

How my limbs move.

I just swung it around to see how far it would move.

The truth was ultimately a distortion.

In the Cheonmachong Tomb, half a tomb? Is that right? The iron cage had woven a twisted passageway into the tomb structure, creating a nearly permanent formation.

In such an open space, fuel was needed to control the flow, and that was the human appendage of Samcheon.

Since it's not going to last long anyway, I'll have to burn as much fuel as possible.

Wouldn't the victims who were used as sacrifices be satisfied in the afterlife if their organs were used to torment their enemies?

Qing creates a new Manra Daehyeolmyeocheonjin.

The time we perceive was also stretched out and pulled.

Let's see, door, shall we put up a door?

And beyond that, well, that might be fun too.

Since the consumption of the offering was enormous, the range of influence was reduced to around the lamas to increase output.

So-called selection and concentration.

Lamas cross an empty land with nothing in it.

Still, his expression was incredibly anxious.

No matter how much I walk, all I see was a horizon stretching far into the distance.

The back of my neck was stiff, so I forced myself to look forward. It was a manifestation of fear, as I tried to force myself to ignore the empty celestial bodies floating in the sky.

How much time has passed like that?

Time passes as the enormous sacrifice was burned and dragged up.

Has an hour passed, or has two hours passed?

It was only when there was no stimulation that people can fully feel the vast flow of time.

In this strange world where nothing changes, even the flow of time seems to have stopped and only seems long.

The lamas' expressions slowly darken.

As he gradually lowered his head to the ground, despair spread through his eyes and they lost their luster.

"[Over there! Over there!]"

When someone shouts, the heads of the lamas who were just blankly following the person in front of them all turn in one direction.

A single screen erected on the silver surface of the water.

The sight of a door standing alone without a frame was strange, almost bizarre.

The intertwined lamas reach the paper gate.

You can examine the paper, but what can you learn by examining it?

However, there was no solution other than opening the door.

I can't just keep walking on this silvery sea of nothingness forever, can I?

Runlin grabbed the door and pushed it to the side, his throat creaking.

Then, a familiar sight unfolds on the other side of the door: the interior of the temple of Hyeolryeumsa Jeokgwangjeon (the temple where the main Buddha was enshrined).

If the door wasn't just in the middle of nowhere, it would be a perfect match for what you'd see when you opened the red-light district gate.

"[Oh, it's a raw fish, isn't it!]"

"[It must have been Emperor Geotap who took action!]"

"[I am alive, haha, Mahavairochanasiya.]"

The lamas enter the door with bright smiles as if they had never been so gloomy.

Then, the mysterious smile of the large Buddha statue in the main hall, Vairochana Buddha, welcomes the lamas.

The lamas collapsed in relief.

Some people dare to lie down in front of the Buddha statue, while others sit down and blankly let go of the fatigue they have accumulated.

Runlin looks at the sight with displeasure, but thinks of the hardships his disciples have endured and endures it.

"[Master?]"

"[Rest. The main Buddha, thinking of what you have experienced, will not consider you disrespectful. I will go and see my emperor.]"

Sometimes there were considerations that were more embarrassing than scolding.

Only then did the disciples, feeling embarrassed, straighten their posture and begin to kneel down in front of the Buddha statue and bow.

Runlin looked at their backs with a pleased smile, then turned around to open the door to the Red Light Hall, but stopped.

Move to the side of the unused door other than the one you just came in through and unlock it, then push the door open.

With the sound of the door opening, Runrin's expression hardens.

Because outside the door, where the courtyard filled with small stone pagodas of the Jeokgwangjeon should have been illuminated, there was only a solid wall.

Knock, knock, Runlin keeps opening the door.

Walls, walls, walls, and finally, when you open the door at the easternmost end of the south side, you finally see the scenery beyond the wall.

Beyond the door was the interior of the red light district.

To be precise, the view inside the Jeokgwangjeon when looking out from the back room behind the Buddha statue in Jeokgwangjeon with the door open, and beyond that, the view inside the Jeokgwangjeon beyond the open door, and beyond that, the view inside the Jeokgwangjeon beyond the open door, and beyond that, beyond the open door… …

The endless red light continued in the shape of a door frame to the far end.

Runlin's fingertips tremble slightly.

"[Master?]"

A lama approaches the shivering abbot, worried, and sees the same figure.

"[Huh.]"

The lama retreats in fright, then, with an anxious expression on his face, opens the doors to the east.

Opening the west gate, the sight of Jeokgwangjeon unfolds endlessly.

Like two mirrors facing each other, the world I see was different, except my image was not reflected there.

The disciples who saw this scene almost crawled across and roughly opened the west door.

Inside the infinite red light field that spreads out in all directions.

And perfect silence.

The lamas had distorted expressions, as if they had lost the way to breathe, in the silence without even the slightest noise—

Knock, knock, knock. The sound of water drops falling.

"[Eek.]"

A lama crawls backwards on all fours, his buttocks creaking.

Bloody tears dripping from the chin of the giant Vairochana Buddha statue.

Suddenly, the expression on Vairochana Buddha's face was filled with hatred.

Knock knock!

In an instant, all the doors close at once.

"[Eek, I'm cursed! This place was cursed! I have to get out!]"

A lama runs away in fear.

As if he didn't even have the presence of mind to open the door, he slammed the sliding door shut and jumped into the red light beyond, then again, into the red light beyond that.

Then, the inside starts to tremble.

An earthquake occurs as thick dust on the rafters falls down, and the ground in front of the main Buddha statue collapses.

A single black flame rose up and settled down, and soon the stench of burning sulfur rose up, stinging the nose.

"[Damn it! Everyone, get your clothes back on! We have to get out of here! Quickly!]"

The hands of the lamas who were hastily weaving the hems of their clothes were trembling.

Meanwhile, the cracks grow larger and larger, and the hole in the Buddha's chamber widens, and some disciples even run alone to the next red light chamber.

"[Quick! Quick! Hurry up!]"

Once again, the lamas, with their robes tied together, leave the red light hall in a single file.

As if waiting for it, a thud thud earthquake follows, and the terrified lamas jump over and over and over again through the gates, crossing countless red light gates and crossing new red light gates.

Without stopping.

Well, look at what they're doing.

Qing giggles and starts to finish.

He cuts his arm with his fingers, sending a trickle of blood down the center of the truth.

The flesh of the victims, the ground meat, and the blood of Qing Dynasty meet, and they begin to burn silently like incense.

Until all flesh was consumed, I will become a true being, and the state of unity of Injin and Jin will be maintained.

Even so, it won't last long.

This was not the time to continue to organize the world while being immersed in the omnipotence of the unity of humanity.

Of course, the feeling of being able to do anything was incredibly refreshing, but what's the point of getting caught up in creating illusions and illusions?

First of all, it's not a place for a child.

Qing looks down at the child in her arms.

As Jin's center of gravity shifted to Qing, the child's face became peacefully asleep.

After carefully supporting the child so that he doesn't wake up, Qing leaves the basement.

But isn't the flesh still burning in the center of the truth?

A situation where the Blood Thunder Demon can see right through me.

All of the Kunlun sect warriors were unharmed, except for a few who were slightly injured.

Even if there were many Blood Demons, there were only four of them, and the rest were not elite warriors of Kunlun.

The best in the world was out there running wild, so if you got hurt in this situation, you would be the one who deserved to be cursed.

So, hello, or something like that.

No, what kind of guy hit that woman in the face?

Your cheeks were swollen and your lips were cracked. Why were you going around getting beaten up when you're at your peak?

(Xue-i-ri must feel very wronged because someone beat her up to make her come to her senses.)

Heemae was so unharmed that she was practically running wild, so wouldn't the Kunlun Sect warriors be glancing at her in amazement?

After seeing the dance of holding the legs of the blood demons in each hand and swinging them with both hands, everyone would look on in awe.

Among them, the expression on Okru Sword's face, with a truly absent-minded expression and a single tear streaming down his face, was, well, amazing.

The mountain was safe.

And on the other side of the Blood Thunder Demon, the masters of the realm were fighting a bloody battle, a bloody battle… …um.

Qing-i watches the high-level battles of the Hyeon-gyeongs from all directions.

The Giant Pagoda Emperor was being beaten like a dog.