\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (20)}

When Qing returned to the large yard in front of Jeokgwangjeon with the child in her arms, the battlefield was already being cleared.

"Kkiaaaak, I'm hungry! Food! Food! Give me food!"

On one hand, a bloodthirsty demon, unaware of its captivity, was making a fuss and asking for food.

That was rather the appearance of a blood cult monster, the behavior of a demon whose brain was dominated by endless hunger, so everyone looks at it with tired eyes and cleans up the corpses of the dead blood demons.

As I was looking at that sight, a hand tugged at my sleeve.

"Miss Ximen."

Xue-i-ri gazes blankly into Qing's arms.

In Qing's arms, there was a little girl who was sleeping soundly.

"Oh, this kid-"

As Qing was about to answer, a question suddenly came in and interrupted her.

"You brave soul. Have you seen any of the mongrels of the Blood Thunder Demon? Why, not a single one. Unbelievable."

Even after the battle was over, Amukhaprap still had a chilling look in his eyes.

It was Amukhaprap who came all the way to Hyeolryeumsa Temple and was unable to find any lamas.

Well, the lamas were lying in ambush outside and were caught in the formation, so they were busy running around like crazy people, tail chasing tail.

Qing was choosing her words for a moment, wondering how to explain this.

Wow! A cheer erupts just in time, cutting off Qing's words once again.

This was the shout of the Kunlun School warriors.

This was because three elders of the Hyeon-gyeong appeared, dragging the Emperor of the Tower, who seemed to have fainted and was covered in blood, with his limbs broken.

It was the moment when the confrontation between the Kunlun Sect and the Blood Thunder Demon Sect came to an end.

----

A group of lamas walks panting like dogs across a land filled with red sand.

In the scorching hot desert sun, I had long since taken off my clothes, and was trudging along in only my yellowed, soiled underwear, forcing my feet into the sloping sand.

Since I was away from the headquarters for a long time, I couldn't get a haircut for a long time, so my hair grew black and now it's hard for anyone to see me as a commoner.

That was when.

Suddenly, the sky darkens, and a huge celestial body casts an ominous starlight across the sky.

In an instant, a huge hole opens in the middle of the desert and swallows the sand flowing in.

Thanks to this, the sand flowed in like a funnel, and the hole was so large that it was a huge anthill that reached ten meters in height.

On that slope, lamas were crawling on all fours, struggling frantically.

But the sand flows so fast and my body was swept downwards that it was difficult to even stay in place, let alone climb up.

"[Gasp, oh, oh, it's falling……!]"

A llama, still of low rank, seems to be overwhelmed and was gradually swept away, desperately holding on to the upper rank's private tutor.

"[Let go, let go!]"

However, the private tutor was also desperate, and he ruthlessly pushes away the disciple who desperately clings to him. In the end, the disciple Rama, who was struggling to breathe in the sand, was swept away and sucked into a hole.

Then a sound echoed from the sky.

[Three offerings.]

The lamas did not understand what the numbers meant.

Until, with a desperate scream, another young monk from the youngest rank fell into the hole.

[two.]

The lamas paused for a moment.

Then, as the body was swept away, it climbs up the rapidly flowing sand slope.

One lama's eyes gleam slyly, and then he pretends to flail his arms and pushes another lama away by tripping over his leg.

"[Oh, no!]"

The lama screams as his legs fly off and he slides down.

[one.]

And then someone screams.

The desperate cries that were rapidly fading away seemed to be fading away.

Pfft. The lamas all strike the ground with their bodies.

The sand suddenly became a solid floor out of nowhere.

The lamas lay on the floor, panting for breath, with no intention of getting up, even though they were sick.

Is this already the tensth world?

When the world changes, even a brief moment of respite was given, and this was the moment we have been waiting and waiting for.

Lying on the floor like that, the llamas look around.

A land where iron handles like hooks rise here and there.

And beyond the steps visible in the distance-

At that moment, goosebumps ran down the lamas' backs.

Because they suddenly realized what kind of land they were standing on.

It was as if it were the top of a giant wagon wheel.

And soon the earth tilts.

The lamas each kick the ground and jump to grab the handle.

And soon, you realize that you don't have enough handles.

The evil spirit paints the world with joyful colors.

… … …

… …

…

It took quite some time for the lamas to be rescued from Manra Daehyeolmyeoncheonjin.

I doubt if it should be called a rescue, but

When the lamas were discovered, they were crawling on their backs, their bellies exposed, forming a large circle in a wide basin below a ridge about twenty meters west of the mountain gate.

Since the masters of Hyeon-gyeong broke the dantian and pulled them out one by one, it was closer to capturing them than rescuing them.

But when he came out of the formation and opened his eyes with a 'huh!', he showed great relief, and even shed tears among them-

"[It was the truth, it was the truth! Thank you, thank you.]"

Even the Kunlun Taoist priest who was tying the lama to him stopped and wondered what kind of terrible illusion he must have been in to do this.

In an instant, everyone had aged by about ten years, so even Amukhaprap, who had been raging about killing them all, was speechless and stopped calling for them to be killed.

Qing was a little disappointing.

It was because they were gradually falling apart, and it was very amusing to see me struggling to survive, even abandoning the family I shared a meal with.

Because of that, the eyes of the lamas looking at each other were full of hatred.

This was especially true because those who dropped out along the way didn't die, so if they hadn't been tied up, it wouldn't have been strange if blood had flowed right away.

But fighting also requires spirit.

The llamas were weak from not eating properly before the ambush and were just holding on with fighting spirit.

In the meantime, they were lost in the formation, so they all started to nod off while locked in the fire pit.

And then, Runlin opens his eyes.

In the middle of the red light, in a bowing posture on a cushion.

"Ugh! Aah!"

Runlin was startled and falls over.

Then, a noise and urgent voices were heard outside.

-[Master!? What's going on?]

Runlin quickly comes to his senses at the sound of his worried disciple's voice.

Then I quickly looked at my body. I was wearing neat clothes and my hair was smooth, as if it had just been shaved.

Only then does Runlin's pulse loosen.

It was a dream, it was a dream.

-[Master?]

"No, it's nothing. Go away."

Runlin sighs in relief after saying that.

I fell asleep for a moment while bowing to my main Buddha, so I have nothing to say about having such a terrible nightmare.

Runlin slowly gropes through the contents of the dream.

And then snickers.

When I think about it, it was an incredibly absurd dream.

Originally, dreams were something that you believed to be real while you were having them, but didn't you realize that they were absurd illusions only after waking up?

And then suddenly, my stomach growls and feels empty.

Has the offering time passed?

Runlin got up from his seat and headed out of the red light district, but stopped short of opening the door.

Suddenly, a feeling of unease came over me. I opened the door and saw that space, that red light, appear again.

Runlin's hand trembles as he approaches the doorknob.

And then, knock!

"Phew."

Runlin takes a deep breath.

Outside the red light, wouldn't the wide courtyard of the mountain temple filled with low towers be reflected?

The last dream was so bad that it became like this.

Huh, it seems I still lack self-cultivation.

As Runrin thought about this, before retreating from the red light, he turned around and bowed to the main Buddha.

The main Buddha just saw me off with a kind smile as usual, and just…

Hard, Runlin's teeth clack together.

Of course, the main Buddha was smiling.

The corners of his mouth rose past his cheekbones, revealing his insides covered in countless beast-like teeth as he whispered.

[You already said you were mine.]

And then bang! Boom!

The sound of a door closing.

Then, creak!

The sound of all the doors opening at the same time.

Runlin's head creaks and turns unnaturally, like a completely rusted iron door.

And the infinite red light transition-

"Huh!!"

Runlin suddenly sits up.

The bright interior of the Buddhist temple with several braziers.

It was inside a Buddhist temple where disciples were lying around in dirty clothes, their limbs tied together, snoring loudly.

The sound of an unknown night bug chirping.

Beyond the screen door, the shadow of a warrior holding a sword was cast by the firelight of a brazier.

"Oh, right. Haaah……."

Runlin wipes his sweat-soaked face.

Yes, we were trapped because that Giant Pagoda Emperor used his tactics by sacrificing us, and we were rescued by the Kunlun Sect warriors.

And then.

Only the body with the broken dantian remained.

But still, wouldn't it be better than wandering around in that terrible formation?

I heard it's a method of the Blood Cult.

At first I didn't believe it, but after seeing the monster called Blood Demon with my own eyes, I couldn't help but believe it.

Emperor Geotap was the last of the blood sect.

So what about Podalap? What about the Great Teacher?

What on earth was going to happen to the West?

Runlin sighs in frustration.

Crinkle, the sound of a night bug crying.

And the Buddhist temple was so hot that it was almost sweltering.

This was because the Kunlun sect warriors had put in a brazier instead of a blanket.

A measure taken to prevent prisoners from covering their bodies.

But there was a limit to that.

Runlin wiped the sweat dripping down his chin, then stopped.

Why were my hands loose?

Runlin looks at his disciples.

These were disciples lying around with their limbs tied up.

But only he has free hands and feet.

Chirp chirp. The night bugs were chirping.

A chill runs down Runlin's spine.

It's still February, what kind of night bug was making a noise in this cold winter?

And squeak.

The sound of a tree leaning.

The walls of the temple lean outward.

And beyond that, the earth of iron-

"Huh!"

Runlin suddenly sits up.

It was a dark, yet familiar space: right on my bed in my room.

Runlin rolls his eyes anxiously.

Is there something strange again? Is it a dream within a dream, am I still trapped in the truth and seeing illusions?

Like that for a long time.

Runlin, who had been looking around anxiously, finally reaches out to the side table on the left side of my bed.

A water bottle in its usual place.

I don't even have time to pour into a glass, so I hurriedly open the bottle with trembling hands.

And phew!

Runlin spits out what he has in his mouth.

Runlin wipes the corner of my mouth, then lowers his gaze, his body trembling like an aspen tree.

Blood welling up on the palm that wiped the corner of the mouth.

The bitter taste lingering on the corner of my mouth told me that what was in the bottle wasn't water, but blood, and fresh blood that hadn't yet hardened.

Suddenly, the room becomes bright red.

A loud noise coming from a very far away place.

Runlin carefully crawls out of bed and peeks his head out.

The landscape below, countless sinners burning on the burning earth.

The hell of Abigyuhuan.

And the ominous whispers of starlight.

[Look carefully. This was the place reserved for you.]

"Huh!"

Runlin suddenly rises to his feet… …

"Ahhh!" "Ahhh!" "Ugh! Ugh!" "Ugh!"

The Kunlun sect Taoist priests frown at the continuous screams and groans.

It's like they're having a nightmare or something, they're screaming all night long.

If Danlun Zhenren had observed the entire situation like Qing, he might have been able to come to a conclusion worthy of being called a Taoist sorcery expert.

The real Thousand-Slayer spirit has entered the method of borrowing power from a fake Thousand-Slayer spirit.

So, the formation was no longer a formation, but rather a realm between the world and the stars, directly connected to the most ominous star.

And Taoism was the art of changing reality through belief.

Even if it was just a show to Qing, what if the Lamas truly believed that they had fallen into the clutches of the Thousand-Year-Old?

Wouldn't you have opened your own upper chamber and accepted the ominous starlight?

No, was it really an illusion in the first place?

Could the ominous star that illuminates the three thousand worlds, the ominous starlight that transcends the great walls of the world, truly illuminate the earth with lies?

Of course, even Danlun Zhenren cannot be sure.

Of course, the Thousand Years' Fortress was a realm of stars, and humans cannot guess it through their thoughts alone.

That was something that only a Danlun Zhenren could say if he knew the inside story.

If he had known, he would have been happy because it would have given me at least a year to think about it.

Qing also didn't know about it.

If she had known, she would have said something like, 'Why were you watching such fun alone?'

Since he didn't know, she just slept soundly.