\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (17)}

The Giant Pagoda Emperor was not running away.

They simply decided to make a strategic retreat.

Who would have thought that those vile political bastards would secretly prepare two Hyeon-gyeongs!

Even the Shaolin monk?

The original plan was to destroy the Kunlun sect and then take control of Qinghai in one fell swoop while Zhongyuan were shocked.

Official?

If you dismiss it as a matter of martial arts, the incompetent and lazy officials of Zhongyuan will not move.

Moreover, if the power of the Blood Thunder Demon was enough to destroy the Kunlun Sect, he would never come forward.

After the Blood Thunder Demon Sect took over Qinghai martial arts world, they established branches in each city and filled them with the best martial artists of the West.

And when the time came to recover Goto, the plan was to rise up in one breath, destroy all Zhongyuan people and traitors, and welcome the liberation army of the Western Zhang.

But more important than that plan was this Giant Pagoda Emperor.

If the first person of the West was alive, he can always aim for the long-cherished wish of the nation again.

But what if the first person to do so dies here?

It was clear that even Podalrap Palace will give up on liberating Qinghae.

So, Emperor Geotap's act of turning his back and moving away now was absolutely not an escape.

It was simply the great determination of a man willing to endure the present humiliation for a greater cause.

The master of the mid-level Hyeon-gyeong has decided to make a strategic retreat, and his speed was like the wind, making it impossible to catch up.

It was Emperor Geotap who was about to climb over the back wall of the Blood Thunder Temple.

The Giant Pagoda Emperor, who was about to kick the ground, hesitated.

It was because of the ignorance that stood on the wall.

But the posture was a bit strange.

Stand on one leg, lift the other leg, and raise the knee to the lower abdomen, folding it like a crane.

And wouldn't you extend one arm above your head and the other arm to the Giant Pagoda Emperor and show him your palm?

It was a ridiculously sloppy posture with no flaws in any part of it.

But what was more shocking than that absurdly strange posture was the fact that Dangjung, who was clearly protecting Kunlun's disciples, had run ahead of me and was blocking my path.

It was known that the state of Wunue was the latter half of Hyeon-gyeong.

Even if it was said to be one level higher than the current mid-level Giant Tower Emperor, isn't it still an incomprehensible speed?

Besides, Ddaengjung was a Shaolin monk.

Although it was said that there was no martial art in Shaolin that was not a divine art, it was not as fast as light art because of the heavy aura like Mount Tai.

The Giant Pagoda Emperor lifts the stone tablet.

If he had gotten ahead of himself and blocked his path, he might have been a more powerful enemy than he was known to be.

Maybe we have reached the next level.

When you think about it that way, even the strange posture of the dangjung doesn't seem trivial.

In fact, you can take it for granted.

Blood Thunder was part of Qing.

And because it was an illusion of the martial arts that Qing created with his true form.

That was exactly what Qing thought the Shaolin monk's cool posture was like.

I don't know much about martial arts, but I vaguely remember the movie about soccer in Shaolin and Mr. Joo's activities.

Stand on one foot like a crane, one hand up and one hand forward.

Isn't it perfectly natural and Shaolin-like?

Of course, absolutely not.

But humans were animals that were wary of things they cannot understand.

Thanks to that, wouldn't the Giant Pagoda Emperor be very tense and have his stone spear in front?

Why can't I feel any movement?

The Giant Pagoda Emperor gulps and swallows.

Could it be that he has reached the natural realm?

It was as if I had become one with nature, like an illusion without substance, and I couldn't even feel anything.

Of course, that's just an illusion without substance.

But Emperor Geotap's guess was also natural.

The Jeongpa guys found the core of the tactic.

But, coincidentally, there exists someone who can communicate with evil spirits, either for a thousand years or for a thousand years.

How could one imagine that instead of destroying the formation, they would have manipulated the annihilation formation of the incomparably evil Blood Cult to create an illusion?

If anyone heard this, they would laugh and say, "Are you crazy?"

That was the moment.

The Giant Pagoda Emperor quickly turned around and swung his staff, "Zzeng!"

Nan-Gong-daero's sky-blue sword collides with the stone wall, creating a huge explosion.

Originally, it was the Giant Pagoda Emperor who should have fought against them, but a master who was presumed to be a naturalist was already watching them.

Emperor Geotap looked over the wall in a hurry, but it was the new form of Wunue that had already disappeared.

Hey, where did he go!?

I'm so nervous!

Nan-Gong Daero cannot understand, but when the enemy was not focused and was stumbling, he takes the opportunity to attack like a storm.

The sword that holds the infinite sky.

There was no obstruction in the sky, so the path the sword can take was also infinite.

The Sword King's sword continues to strike the stone wall, creating a loud noise.

The Giant Pagoda Emperor looked around, rolling his eyes in search of traces of Wunue, and he was busy retreating and striking Kanggi.

moment-

"Noom!"

Emperor Geotap places the stone tablet and claps his hands vigorously.

Then, a bloody sphere of energy exploded in all directions, gaining momentum!

Nan-Gong-daero immediately opens the street.

Then, the Giant Pagoda Emperor, who had picked up the stone tablet again, suddenly shouted.

"Cowards! How can those so-called "Jeongpa" act so vilely! Why can't they attack them one by one, fair and square? How can the majority try to persecute one person?"

"Of course, eradicating the evil cult of the Blood Cult was something the entire martial arts world can do together. It's about defeating evil and establishing justice."

"My junior was right!"

The sharp sound of a blade cutting through the wind.

Seven daggers, each emitting a sunset-colored energy, rush in a row toward the Giant Pagoda Emperor.

In an instant, the daggers all point downwards, forming the image of seven powerful swords sequentially cutting down the enemy.

match!

The Giant Pagoda Emperor applauds loudly again.

A blood-red stream of energy that rapidly expands into a hemispherical shape.

The seven daggers hurriedly turned and returned in one direction, forming a formation above the head of Ximen Surin, who had already landed on the ground.

Qing failed to hold back her admiration at the sight.

Wow! The winning sword! Wow! The battle hairpin!

Wow! Master, you were so kind!

The identity of the daggers that were striking the Giant Pagoda Emperor was none other than the specially made battle hairpins.

Thanks to all the hairpins being pulled out, the Master's hair was loose and wavy like silk, and she looked like a painting of a beauty.

You look beautiful from the front, you look cool from the back, you look manly from the side, and when you look at it from above, um, from above, um. You were a beauty.

Qing's heart was pounding with excitement as if she's craving fried corn.

Finally, isn't this the beginning of the battle between the true transcendent beings?

but.

"Despicable, despicable! Han, how! Just one! Damn it! One on one, talk to me! You bastards!"

"No questions asked!"

It wasn't the picture that Qing had in mind.

The Giant Pagoda Emperor completely lost his momentum.

Not only was the Sword King not enough, but a female mad dog was also a villain!?

Of course, Mubul among them had not yet joined in as he was busy fighting the Blood Demon.

For the Giant Pagoda Emperor who believed in illusions, there was no choice but to think that he was hiding somewhere and waiting for an opening.

So, while the invisible thief was concerned, the mean mad dog just keeps swinging his dagger from afar.

In the meantime, a child who was still in the early stages of development fearlessly stretches out his sword.

Normally, I wouldn't tolerate this arrogance, but I couldn't afford to do that to the Giant Tower Emperor, who was fighting two to one, or three to one in my experience.

So, blocking, getting hit, getting cut, throwing myself, rolling, jumping up, clapping, rolling around, getting hit, flying through the sky, clapping, flying a blood seal, dodging a dagger, shaking my waist left and right, using the technique of the iron plate bridge, I lay down, and in front of me was the sunset-colored steel energy that was piercing down, and just like that, I fell to the ground with my back and rolled again.

This was how you know who the bad guy is.

He was the Giant Pagoda Emperor who was happily getting hit, rolling, and flying around.

It's so miserable that it almost looks pitiful.

Still, he was a master of the current situation and somehow manages to avoid fatal injuries.

But isn't the fact that the gaze doesn't die like the eyes of a lynx that constantly looks around for an opening?

The Giant Pagoda Emperor has this!

These damn bastards! I'll shorten my lifespan and send one or two of them to hell!

It was the moment when the Giant Tower Emperor, rolling on the floor, pulled out his true origin and stretched out towards the water with a powerful flow.

Suddenly, a giant Buddha face appears out of nowhere, filling the field of vision!

Of course it's a fantasy.

It's obvious that they're preparing a vicious method of saying, "You die and I die."

Huh. I can't just leave it alone.

It was not the Buddha's face that was important.

The important thing was that it suddenly appeared before your eyes and filled your field of vision.

The lifespan that the Giant Pagoda Emperor painstakingly chose, the precious true source, was being harshly struck down on the innocent land.

In the reaction, one of the swords jumped up, and seven battle hairpins were stuck one after another in the spot where they were lying, just a hair's breadth away.

Qing creates Buddha again.

The Buddha stood before the flying pagoda emperor.

He was a strange Buddha who would look at me with his uniquely kind smile from a position where our noses would touch, and even if I turned my head, he would persistently follow me and make eye contact.

Only then did Emperor Geotap realize the situation.

Fantasy! Jin has been taken!

"conflict!"

Emperor Geotap's martial arts, contrary to his humanity, were truly Buddhist martial arts.

At the shout imbued with the spirit of the enemy, the formation quickly loses its shape and disintegrates, disappearing.

Then, as if they had been waiting, Ximen Surin's battle hairpins flew in.

Of course, the two masters of the scene also saw the back of the Buddha's head suddenly rising and covering the face of the Giant Pagoda Emperor.

But that's it.

Would Qing have created the image of Buddha for nothing?

If you call out the ghost's face, both elders will hesitate and be reluctant, thinking that there was something they were going to say, so it was Buddha who found something familiar and kind.

The Giant Pagoda Emperor wears a golden scepter on his body.

Qing felt the influence of the distorted and broken formation around it.

I guess it means that the appearance of Buddha before my eyes was that fatal.

But enough was enough.

I feel satisfied seeing one person being chased by two people, and a new person appearing from all directions at the same time.

What if even Monk Wunue came?

I've done my job, you know.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Just a moment ago, Emperor Geotap was frozen in fear after seeing the illusion of Wunue's figure.

Qing was looking at all places from all directions of the formation simultaneously.

I don't know how that's possible.

But if you know it's possible, why do you need to know it?

Just as the arm moves, there was no reason to know how it operates.

The lamas of Blood Thunder Temple were dumbfounded.

The sea of emptiness, a concept that people of this era had no idea about, and the shape of a gigantic celestial body in the sky.

I was left helpless, my eyes fluctuating in the face of the overwhelming mass that was endlessly reducing me to something small and insignificant.

Some lamas just kneel on the flowing ground and gape stupidly.

That was the moment.

"[Lee-ik, can't you come to your senses!? How long were you going to lose your mind!]"

There was someone who shouted as if he would not give in to fear.

His eyes were shaking dangerously, his teeth were clenched, and his fists, clenched so tightly that they were bleeding white, still trembled slightly with fear.

Nevertheless, the will to overcome was resolute.

It was truly a heroic emergence, a remarkable will that was like no other savior in troubled times.

It was Runlin, the chief priest of the Blood Thunder Temple.