\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (6)}

Xinying was full of energy during the Lunar New Year.

The reason many cultures celebrate the New Year in the middle of winter was because they have nothing better to do and were bored at that time.

It was a difficult time for farmers, of course, as the ground was frozen and construction was difficult. It was also a time when even those who entertain guests were deserted as there were few tourists in the cold midwinter.

The loggers who cut firewood must be sweating a lot, but even in Qinghae, trees were rare and it was prohibited by national law.

In that respect, the custom of welcoming the New Year in spring was a rare case.

I'm so busy in the spring, what kind of holidays were there? In fact, the new year at the Xijang was celebrated quite modestly.

The New Year in Xinying, the largest city in Qinghae, was not as extravagant as in Jungwon.

Unlike the Chinese New Year in Zhongyuan, where people dress up in colorful, flamboyant cotton clothes, they wear dull, thick, puffy fur clothes and turn their fur hats upside down.

If you wear Qinghae fur hat upside down, you will look like a group of robbers with holes for eyes and mouth.

But still, it was full of energy.

The exposed eyes were so full of laughter that the corners of their mouths were heavy and lopsided, and the corners of their mouths were turned up towards the sky, revealing their bright teeth.

Children run around making their own unique chirping sounds, and somewhere, the sound of drums and gongs rings out loudly.

A lion dance performance was in full swing in the square.

With red lights hanging from the ropes all around, illuminating the early night, the lion's head shakes and its tail sways, performing a cheekily and sly dance.

And then we went on a full-scale night tour.

Qing walks through the night with her master's arm linked.

The streets were filled with cheerful greetings like, "Happy New Year!"

At this time, both street vendors and customers greet each other with raised voices like a merchant, as if the entire city was wishing them good fortune.

Qing buys a gourd filled with cheap milk tea and sips it.

The pumpkin was a symbol of good fortune, so it was a common snack you can see at night during the Lunar New Year.

Then Ximen Surin's eyebrows twitched.

"How can a woman walk around and drink alcohol while standing? How can Disciple be so crude?"

"Hehe, Master. Isn't the bigger problem the perception that men just drink and go around, while women should be ashamed of being seen? The world's hearts were set on men, so when a man drinks, he's wild and brazen, and they praise him as a hero. But don't they point fingers and criticize women for taking a sip, calling them unruly? I believe the world is narrow-minded, and therefore, as a master of women's drinking, I believe I should step forward and act as if it were the right thing to do."

Ximen Surin's still hands clenched into fists.

Was the anger bar that appeared after a long time going to break again?

"What on earth were you talking about? What Disciple said…what Disciple said, Hmm. It's very logical and concise."

Ximen Qing has poisoned Zhongyuan again!

"Yes, Disciple is quite right. Even women who love alcohol pretended not to drink, just having a couple of sips, and then retreat to drink in secret. What kind of unreasonable thing is this? Shouldn't the female masters act as my disciple suggests and change the situation?"

Qing just wanted to sip some alcohol and browse the night market.

So, the teacher and student walk through the night on the Lunar New Year's Eve, arm in arm, holding a gourd in one hand and sipping it in the other.

We ate lamb skewers, mou skewers, pork skewers, and since it would be a shame to only eat oily food, we also ate tanghulu, which was dried hawthorn berries frozen in water, and wonsongbyeong. Oh, I don't know why wonsongbyeong was sold during the Lunar New Year, but it was sweet and delicious.

The nights were long anyway, and Xinying was one of the proud metropolises known throughout Zhongyuan.

The Lunar New Year was a time for fun, but it was also a chance for everyone to make a little money in the middle of winter, so wouldn't the street vendors be endless?

However, instead, the street vendors were all there.

Sell ​​the things you already have, and sell them again.

So, even after the liquor that was being sold has run out, there was always a street vendor selling bokbyeongju nearby.

The number of empty gourds was one, two, three, four…

"Hmm, Disciple. Look at this. Isn't it really beautiful? The threads were carefully dried and woven, showing great care. Little child, how much does this decoration cost?"

"Oh, that's-"

A little girl who was selling decorative plate rolled her eyes.

A rather clever look in her eyes, as if she were trying to decide whether or not she should take advantage of then.

Then I saw Qing's appearance. It was a cold night, and she was a woman who had taken off her hat and only covered her face.

With each hairpin attached to a dozen or so ornaments, and all sorts of other things hanging from the top of the head, it seemed like I wouldn't be cold even without a hat.

That figure must have robbed several trinket stalls by now.

Isn't this really a tough situation?

"Uh, fifty-"

"Ahhh!!"

In an instant, a man passing by screams and spins around five times before falling and rolling on the ground.

When Ximen Surin lightly tapped the man with her toe, wouldn't colorful pouches pour out from her sleeves and bosom?

How to make someone rip their pockets clean by poking them in the side.

Even if Qing watched from the side, he couldn't tell.

One of the bags floated up and flew quietly into Ximen Surin's hand.

"Tsk tsk. Even on holidays, thieves were rampant. So, child, how much did you say it was?"

The girl gulped.

She spoke, her eyes spinning like a dragon's wind, looking back and forth between the man lying on the ground and Ximen Surin.

"Ten doors, ten doors."

A girl with a jewelry arm who suddenly regained her conscience.

"Really? Considering all this effort went into it, aren't you selling it too cheap? This, this, yeah, this, and these are pretty, too."

Ximen Surin takes out only the well-made decorations and hands the coin to the girl.

The child's expression brightened when Ximen Surin said that she could keep the change.

Ximen Surin began to hang one more on Qing's head with a faint smile that was unlike his usual solemnity.

The head was full of decorations, so there was not enough space to hang them, so now the Ximen Surin was hanging down to the front of the head.

"Master? If you keep doing this, I won't be able to see ahead."

"What's the problem with this master right here? Come on, let's go. How can a woman be so skinny? You said you were ordered to go to the Repentance Hall and reflect, but did that Tian Feizi bastard even feed you? My disciple's face is already half gone. Eat and regain some energy."

\textit{I can't tell where the skinny part is though.}

\textit{But now I know one fact.}

\textit{Master. You are weak to alcohol…}

\textit{But if Master says so, then what was it?}

\textit{I guess I'll just let Master enjoy it.}

\textit{Anyway, if it's Master, she can expel alcohol in an instant and return to a clear mind.}

Qing starts walking, led by her teacher's arm.

Because of the weather, the wind was blowing through my skin, so I can barely use my Awakening Divine Skill's spatial perception, but I can still set foot on the ground.

"Come on in, are you sisters? Oh, my. Hmm."

It was a snack vendor who had an expression of "Oh no."

Of course, the woman who was being led away with her arms linked would have covered her eyes with all kinds of decorations.

Tsk tsk, how did it end up like that?

Wouldn't it be unusual for merchants to be particularly kind, choosing the biggest one for you or even giving you a bonus?

On the roadside, musicians pluck strings, play flutes, and sing songs, enjoying the rare peak season that lasts only a few days a year.

The focus of the decoration fluttering in front of Qing's eyes spreads and Ximen Surin's smile seeps through the gap.

\textit{Um, Master, aren't you drinking a little too much?}

\textit{If you think you're too drunk, you can just expel the alcohol, right?}

Anyway, the night deepens.

It was a night of the Lunar New Year, with fireworks in full bloom.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Arabdal-Taek Buddhist Temple, also known as the Blood Thunder Temple, was located on Mount Ahabrabdal-Taek.

It was the source of the Yangtze River and has been a sacred mountain for the people since ancient times (Qinghai was originally the land of the West Tibet).

Seongsan means holy land.

So, Runlin, the head priest of the Blood Thunder Temple, has been feeling quite uneasy lately.

Dozens of rascals, obviously rude, had set foot on this sacred land.

Those scoundrels keep going against my will, so even if it's Podalrap's will, I can't help but feel hurt.

Look at it now.

"[You guys! How can you not even take off your shoes in front of the main Buddha?]"

"What? I just came because the Emperor was looking for me, and you want me to take off my shoes in this cold?"

"[What the heck, what the heck-]"

"[You're wearing thick socks and telling us to show our bare feet?]"

"[No, what kind of guys were these……!]"

Countless tendons sprout from Runlin's bald head.

There was no such law in the world.

Not only in the West, but also in Zhongyuan, when entering a temple to see the Buddha, don't they take off their shoes and go up to the temple to clean up their demeanor?

But what on earth were these guys!

How can these guys accomplish such a great feat? No, no.

Runlin exhales deeply.

The tendons that sink into it.

but.

This was not because the anger has subsided.

I must open my mouth today and teach these ignorant and rude bastards a lesson.

Rather, he was so angry that he decided to kill her, but he calmed down and decided to kill her.

So Runrin puts his hands together.

And that was the moment when I stretched out both hands and was about to dismember this ignorant, vicious man into pieces of meat.

-[Oh, please be patient for a little longer.]

The sound of the waves echoing from all directions.

A six-way battle! The sound was transmitted, but it was a sophisticated technique that simultaneously surged in from all directions (plus above and below) without the messenger's location being known.

-[They deserve to die, but they were nothing more than expendable weapons to be used as swords in the fight against Zhongyuan. Calm your killing intent by thinking of the greater cause and righteousness.]

That was why these ignorant people were stepping on sacred ground.

Runrin barely managed to control and suppress the killing intent he had decided on.

Then we head to the inner room deep inside the temple.

Inside the inner chamber, there was the figure of Emperor Geotap with a brilliant golden halo behind his head.

No matter how many times I see it, it was a wondrous radiance, the light of enlightenment radiating from the early disciples of the present world.

"Your Majesty, how long will it take for those lawless bastards to be released? The Zhongyuan' Lunar New Year was only five days away. Shouldn't we get rid of those blasphemous rascals from Kunlun before then?"

"[Foolish. Even if Kunlun was a wicked group that deceives the world with false doctrines, its history cannot be ignored. Invading the Kunlun sect was the worst of all evils. How many devious defenses must they have erected in their nest?]"

"[You said you wouldn't clean up the mess-]"

"[It's all your fault. The bastard you missed has already joined the Kunlun Sect.]"

"[Are you saying that Yahipa ran away to the Kunlun sect!? Your Majesty, then, the Vajrayana monks who were pursuing him—]"

"[I heard that he was brutally murdered and hung, so he didn't even eat animals, and so he couldn't even bestow his last virtue. Wasn't this due to your poor skills?]"

Runlin shut his mouth tightly.

Then the Giant Pagoda Emperor clicked his tongue.

"[They'll be on their guard now. Is it a good strategy to rush an enemy who's already prepared?]"

"[If that Yahipa bastard had told us about our great undertaking, wouldn't the Kunlun bastards have invaded?]"

"[Yes, that's exactly it. I understand you're the only expert at headquarters right now. So, after the Lunar New Year, I'll lead my disciples and attack.]"

"[Then the damage to the headquarters-]"

"[Go! You idiot, what have you got to fear from a mere Kunlun? There were no true masters in Kunlun. What do you care about a few Hwagyeongs?]"

And then the Giant Pagoda Emperor speaks with a rough, evil, and bloody smile that does not match his brilliance.

"[Isn't this the very seat of my throne? We were strong, and the enemy was letting down his guard. So, fear not. The moment these detestable invaders of Zhongyuan reveal their true colors, that will be the moment when they were judged for their past sins.]"
