\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (10)}

Today, Qing was practicing his internal energy in the cool DaeQing.

Of course, even the luck was so mean. I close my eyes and think, what's for dinner tonight? Sweet, simmering meat, yes, it feels like beef. I have a feeling it'll be beef today.

Whatever his true intentions, to others he appears to be wearing a golden halo and a gentle smile.

Isn't this the appearance of an orphaned master?

This was the reason why Ximen Surin suggested to Qing that he come out to the main hall and do a ritual so that all the villagers could see him on this cold day.

It could be an example of a female master, or something like that, but it wasn't forced, it was a gentle suggestion.

Anyway, since I'm wearing a fur coat and a hat pulled over my head, leaving only my eyes and mouth exposed, it's not that difficult to exercise outside.

As I was doing that, I heard an exclamation of "Oh."

When Qing opened her eyes, wouldn't the stranger smile shyly?

"Did I interfere with your training?"

"No. I'm starting to feel uncomfortable sitting still, so I'm trying to move around to loosen up. Your Majesty—"

"Oh! That went well. Want to spar?"

The expression on his face was like, "Huh?"

It's not like he really tried to move his body, it's just a nice way of saying that he wasn't bothering you and not to mind.

But before I could even finish speaking, we had a sparring match?

I don't even know who you are, but all of a sudden?

Qing looked at the unfamiliar middle-aged man.

There was a feeling of familiarity that comes from seeing a stranger for the first time.

What, where have I seen you before?

Then, behind that head, familiar objects with a bang appeared.

A handle made of black wood with a thin leather cover.

It was the very same wooden sword that Geomwoo always brought from somewhere for training. Wouldn't a middle-aged man have six or seven handles?

And then, three exclamation marks, symbols of his hometown, came to mind.

"Uh, by any chance, Sword Friend, I mean, Shencai-"

"Haha, you have a good eye. Doesn't that guy look just like me?"

"Ximen Qing greets elder Sword King."

"There is a separate way for swordsmen to greet each other. Here."

A wooden sword was pulled out from Nan-Gong-daero's back and flies into its owner's hand.

And a wooden sword that draws a parabolic curve when thrown.

Qing accepts it, and, um, Geomwoo's eccentricity and Dalian Gwang were not for nothing.

I make a rational inference that maybe we just grew up seeing it and took it for granted.

By the way, it was a situation where the expert side was recommending sparring for a long time.

In the martial arts world, this usually has two meanings.

first.

I'm going to beat you up legally now.

If you refuse or try to run away, you will be beaten more, so just take the beating quietly.

And the second was a sign of great goodwill.

Because there's nothing to gain from fighting with a lower class anyway.

If beating them up isn't the goal, it means offering to teach them a lesson.

"Then, I will gratefully accept it."

"Okay. Okay. Come."

Nan-Gong-daero takes a step back and takes his place in the center of the guest house courtyard.

Qing slowly examines his opponent.

In fact, wasn't Nan-Gongga's swordsmanship something we'd already seen enough times to be bored?

Even the Emperor Sword, which was said to be the essence of the martial art that only the direct descendants of the family could master, was stolen and learned.

I think you're probably thinking of countering with the Emperor's Sword.

Qing looks at the Sword King with serious eyes.

Qing already knows the Emperor's Sword very well.

The art of nullifying enemy attacks and further harming them through the best trajectory.

A latecomer, a dull sword that pursues the principle of reaching out later and reaching first to the extreme.

So, when giving a trajectory, the straight line to avoid the most was the crosscut.

Because it was easy for people to dodge by moving left and right, but there was a limit to how much they can move up and down.

"I'm going!"

Qing ran towards Barak, shouting.

The figure of the Sword King rapidly approaching.

The blue sword swung left and right, and it looked like a child swinging a willow branch without knowing what was happening.

"Good!"

The Sword King was greatly impressed.

It may not seem like much, but if you were the Sword King, wouldn't you be able to see into the sword world as well?

The black ironwood sword was actually heavier than a real sword.

Yet, the trajectory of the tiny circle that circles back and forth was evidence that it was not swung by force alone.

It means that you fully understand the kind of lofty new skill that breaks the established format.

Indeed, peers, no, does peers make sense?

If we were on the same level, there will be no one to rival us.

However, to a master swordsman who had dedicated his entire life to swordsmanship, that weakness was also clear.

The moment Qing's foot was just one step away from the sword's distance and territory, Nan-Gong Daero's wooden sword flashed.

It was the moment when a clear straight line pouring from the upper right to the lower left, the only correct answer among the infinite sword paths, was revealed to reality.

In an instant, Qing's eyes flashed!

The footsteps that were running towards me hit the ground with a bang! A huge rumbling sound shook the earth, and invisible concentric circles spread out in all directions.

One step, trampled with all your might.

I've trampled on it with all my speed, so all the running I've done so far has been nothing more than a run to get to this one step.

And then bang!

A second ground cloud, supporting the body leaning to the right, follows the first concentric circle that has not yet spread out, with a misaligned center.

A single, desperate step forward, filled with all your strength.

The tip of the blue sword pierces the sky.

The Sword King's eyes open wide.

A new form of blue that stretches out the moment the wooden sword touches it.

The Sword King's wooden sword cut through the air, and then… bang!!

"Gasp!" "Gasp!"

The former was the voice of the Sword King, the latter was the voice of the Blue King.

Because the blue wooden sword hit Nan-Gong Daero's side of the head.

"Hahaha! You punk! Look at this!"

Suddenly, a hearty laugh rings out from him.

Wouldn't Master Wunue, who had been sitting in the main hall, burst into laughter and pointed at the person who had arrived?

Ximen Surin, standing next to him, nodded to her disciple with a very satisfied smile on her face.

But Qing was anxious.

Well, it she had just smashed her friend's father's head on the temple.

"Oh, okay, were you okay?"

"Ugh, this really hit the mark."

"Oh, sorry."

But a bright smile spread across Nan-Gong Daero's face as he grabbed the side of my head.

"No. I underestimated you because you were young, and I was caught off guard. It's because you did your best. If you're going to apologize, I should be the one to apologize."

To be honest, Nan-Gong-daero underestimated Qing.

And since Qing regarded the Sword King as a master, he knew how to deal with him, whether by avoiding him or counterattacking.

"Yeah. If that guy named Hyeon-gyeong got beaten up by Hwa-gyeong, then of course he should feel sorry. Isn't that right?"

Although Ambassador Wunue teased him, Nan-Gong Daero paid no attention to it at all.

"You must have guided my swordsmanship by seeing the swordsmanship of the new kid! Your swordsmanship was truly magnificent!"

Just a refreshing, cheerful smile.

"I was curious when I heard you were called the next best in the world, and I see that the assessment was indeed correct. As my senior who wields the sword, how can I not be happy about this! It's time for Shaolin to step down from the top! Yes!"

After all, with the exception of the Great Emperor Mucheon and the four Heavenly Horses, the position of the best in the world was essentially a monopoly of the Shaolin monks.

"This kid. There's nothing he can't say in front of his senior. Are we going to grow old together?"

"Did I say something wrong? Don't you think so too, Senior Ximen? A world where the greatest swordsman in Wulin is the greatest master of Wulin—isn't that the right world?"

Ximen Surin also nods his head at him.

"Why is that Junior saying such a good thing?"

"What's the right word? It's a bit of a slap in the face. The inspectors were really excited."

Qing sneakily looks around.

I hit my friend's father on the head, but the atmosphere was pleasant and I felt relieved.

"Disciple's swordsmanship is truly remarkable. However, when facing a master of the Hyeon-gyeong, there are places more suitable to aim than the head."

It was not a good decision to aim for the head.

For Hyun-kyung, who was dealing with sewage, the head was no longer a weakness.

The skull was the third hardest bone in the human body, and because it was divided into several parts and has a rounded structure, it was actually the part with the strongest protection.

How about adding self-defense skills to it?

In fact, even if Qing had held a real sword and had been strong, he would not have been able to pierce it, but would have left a deep scratch.

So, the Sword King didn't bother to forcefully block it, because if he showed his true feelings, Qing would get hurt, so he decided to just accept it.

The disciple was given a stern admonition not to be proud.

However, the expression on Ximen Surin's face as he spoke was so innocent that it was not very convincing.

Well, in a swordsmanship duel, he was the disciple who struck the Sword King's head. What a remarkable sight that must be.

Anyway, the Sword King raised his wooden sword again and said.

"I guess I have to be sincere from now on."

Qing carefully observed Nan-Gong-daero's expression.

What was it that Hyeon-gyeong's master was putting all his heart into?

You're not the one who has a bad temper, were you?

It's like getting beaten up and stuff.

But the master was still here, um.

Now that I think about it, if it was Master's educational policy, I don't think he would really care even if he got hit, broke, and rolled around.

For a moment, Qing worried that this might be revenge.

"It was good just now, but from here to here, like this, this movement seems like a waste. Was it meaningful?"

"I understand your strength was formidable, but excessive force can ruin your skills. It would have been far more threatening to target the three sides instead of the river."

"Hmm? Just try the check again. Oh, right, twist your wrist a little more. Yeah, that's how it should go. You're so strong, you've got some bad habits here and there."

What was this comfort?

Qing blinked her eyes.

The Sword King's sparring was the complete opposite of his master's.

Ximen Surin's sparring can be summarized as, "Don't you know? If you don't know, you have to be hit."

You just made a mistake, but you don't know you made a mistake?

Then it must be right.

I just had a bad habit, don't you know?

Then it must be right.

I don't know why I just got hit?

Then you have to wait until you find out.

Compared to that, the Sword King's training was very much like that of a kind teacher. Whenever something needed to be pointed out came up, he would immediately stop and explain, and then continue to repeat in a way that improved things.

I thought that the way Geomwoo explained swordsmanship was really easy to understand and excellent, but it turns out that he learned it all from his instructor, Chun Bujang.

Even.

"Wow. The swordsmanship changes freely, so it's quite powerful. It seems you haven't yet grasped the implications of that swordsmanship? It's better to keep it in mind, as it could actually be poisonous against a skilled opponent."

The swordsman's eyes winked as he spoke of that sword technique.

It was also a sign that he recognized me, as I had been the first to use the Baekpalsura Sword without even realizing it.

What was it? You're doing such a great job.

Well, that's my friend's father.

I'm probably one of the few close friends and confidants of Geomwoo, so he might treat me well.

Well, to Nan-Gong Daero, Cheonhwageom was not just his son's friend.

If I had to say, he was closer to a benefactor.

A person has two arms, one to hold the sword and the other to assist.

But the crazy bastard didn't even try to use one arm, so wouldn't a guy with two arms look like he's one-armed?

So, I feel sick and tired.

I tried to appease him with alcohol, but the hot alcohol burned my stomach, making it even more bitter, and I kept worrying about drinking again.

"You keep talking about the double sword and all that other crap, but thanks to you, that foolish brat has come to his senses. You saved one person, and I was on the verge of dying from a broken heart, so you saved two people."

Ambassador Wunue was chattering beside him.

"A two-handed sword? You're saying that someone who can barely walk can fly?"

"Oh my, Senior. I'm dying. If you're going to find your sword, shouldn't you at least reach Hwagyeong, at least the latter half, and then use the first technique again? A guy who can't even do one thing properly was making a fuss about trying to do two."

It was the Sword King who immediately complained to Wunue, as if he still had many things to be sorry about.

"Ahem."

In reality, when I actually complained, I couldn't tease him anymore.

Well, a truly painful wound was not something you can joke about.

"So, please take good care of this unworthy son of a bitch. He needs a lot of prodding from the side to wake up, so before you go anywhere, make sure to send a message to Segaro first. I'll send him over, so if you take him with you, I'll be happy to hear your wishes."

I asked why you were being so kind.

They say there was no such thing as a free lunch, but this was the Sword King who made a truly serious request.

Then Ximen Surin clicked her tongue.

"How can a mature woman walk around with a man by her side?"

"Oh, my dear, Senior. That's not it. Of course, if Cheonhwageom had the heart, I would take her as my daughter-in-law even if it meant carrying her. But first, let's help that crazy brat come to his senses."

"Hmph. But how can you, when the world was watching? If a woman hangs out with a man, isn't that a present fault, a past fault, and a future fault? How can you possibly just gloss over such a request after a few rounds of sparring?"

Ximen Surin clicked her tongue again as if she was displeased, and then said.

"At least teach her a few tricks. How can a man be so shameless?"

"I was thinking about that anyway. Senior, I'm not that shameless."

In the end, this was the main point.

Teach her something decent instead of just sparring.

Wunue smiles brightly at her.

If it were like before, wouldn't Ximen Surin have immediately thrown a punch?

Still, didn't she learn to endure it and ask a favor for the sake of her disciple?

It's an amazing transformation of the fierce female dog.

So, isn't this the greatness of fate, the bond that binds people together and makes them live together?
