\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (16)}

Goooooong… …!

A faint sound spreading far away in the sky.

But as soon as you hear it, you realize that it was an eerie, infinitely huge sound.

At the sound of the sky falling, everyone, human and demon alike, looked up to the sky.

All eyes were wide open, veins were visible in the whites of their eyes, and dark red blood was spreading.

As cracks form inside the pupils, three or four of which were positioned in the eye sockets, new eyes open, and it seems as if ten million pupils were sweeping the world at a speed that leaves afterimages.

In that moment, everyone realizes it simultaneously.

That was the star, the evil star that does not exist in this world, the madman who laughs with his eyes torn apart.

In addition, countless hands stretched out from the fleshy earth, stretching infinitely towards the sky.

"Hey-!" "The sky was falling!"

The ugliest star in the sky was falling.

A strong malice that threatens to destroy the world.

The earth begins to disintegrate piece by piece, and everything begins to float into the air along with blood.

The world's most ominous star sheds tears of blood.

Blood flows from tens of thousands of eyes and spreads in all directions.

The blue of the sky has disappeared, and all that remains was a sea of rotting blood above your head.

Then a crack appeared in the sky-

"Ugh!" "The sky, the sky was falling!" "Everyone, everyone was going to die! Oh Primordial God!" "Heh heh, heh heh heh……!"

The expressions of the Kunlun warriors were distorted.

Someone falls to their knees, bows their head, and sobs.

Someone was grabbing my hat and screaming at the top of their lungs.

Some people look at the end of the world with ecstasy, some with despair, some with sadness, some with depression, and some with emptiness.

But the results of other emotions were the same.

Eyes that have lost their luster and were dead.

The moment each of us lets go of the weapons we hold-

"Gaal! Come to your senses!"

Pure words sweep through the room.

Then, a light flashes in his eyes, but only for a moment.

!!!!!

With a cracking sound felt in the soul, the sky that had finally cracked shattered into pieces.

Then, putrid blood poured out like a dam had burst.

Crimson blood falling in a waterfall larger than the world, and palms stretching out towards the sky.

"Ah, no……!" "Ahhh……!"

Again, deep despair spreads through the crowd.

If those two meet, if they meet, something very big, something incomprehensible that cannot be understood by human reason, will happen.

That is, the most hideous, the most vicious, the most ominous, the most disturbing, the most terrible of all apocalypses.

Finally, the two meet-

And nothing happened.

The person who had been sitting down in despair slowly stands up, holding the sword.

The person who was crying in despair wipes away his tears with an embarrassed expression.

The person who was desperate and screaming pretended to clear his throat, which smelled like iron.

Suddenly, the sky brightens to a clear blue, the earth returns to its original rock, and the neat temple of Hyeolryeumsa with its white walls and blue pigments looks as if it had never been like that.

"What!" "I don't know!" "I'm hungry! Food!"

The bloodsucker immediately cries out in hunger.

The Kunlun warriors suddenly came to their senses at the shout, but it was already too late.

The moment when the blood demons jump up and rush towards me.

"Take the sword!"

At that moment, the person who jumped out stretched both arms forward powerfully.

At the same time, the golden energy becomes a huge barrier that repels all the blood demons.

Great Power Diamond Hand

The Dharma of the Diamond Sutra, the Diamond Sutap

The bald head was particularly shiny.

It was the departure of the best person in the world who no longer needed to maintain the afterlife.

Oh. What was that?

Qing was amazed without realizing it.

Since the Manra Daehyeolmyeocheonjin was inside Qing, Qing could view the great study from all directions.

Even if it's a review of the current situation, isn't that completely different from martial arts?

What kind of person builds a wall by himself?

Of course, the duration of the barrier was only a short time, barely three digits, and it wasn't a lethal technique.

The brilliant golden barrier merely roughly repelled the bloodthirsty demons, and the monsters that had been rolling on the ground suddenly rose and looked ahead with fearful eyes.

It seems that Master Wunue was also a monk, so he learned teachings about immortality and such. Oh, that's not it.

Next, the best person in the world shows off his dance skills.

With one swift punch, the demon's head vanished again, and after a few blows to his ankles, the demon rolled on the floor with both legs severed.

The whole body was literally a weapon.

It was a one-sided fight that didn't even show any strength.

Is that all?

If you throw a punch, the head of the blood demon ten steps away will disappear.

If you point with your finger, the head of the bloodsucker fifteen steps away will disappear.

Each of these techniques was called Baekbo Shinkwon and Geumgangji of Geumgang Daeryuksu, but to Qing, the achievements were so far-fetched that he cannot even tell what kind of martial arts they are.

However, there were two advantages to being a bloodsucker.

One. I lost my sense of fear.

Two. And there were many of them.

A hundred or so men, without even a shred of fear, rushed forward, intent on satisfying their hunger. The warriors of the Kunlun Sect split left and right in their valiant efforts, eager to fill their bellies with flesh.

However, the Kunlun warriors had already formed their formation, and under the shout of "Advance!", they clashed with each other in a busy movement.

Qing sees the inside of Jin everywhere.

And from the inside of the truth, we also look outside.

Then, Qing sees, feels, and perceives new things.

Jin was the inside and outside of Qing.

The law itself was one.

Qing realized it very naturally, as if she had known it from the beginning.

This system was now mine.

I can do whatever I want.

At that moment, there was a strange gaze.

Qing turns his head (up-down-left-right-turning) and looks in all directions, looking at the evil star with a strange gaze.

What, do you have something to say?

Then the most blasphemous star turns its gaze.

He's been doing this all along, but it would be most accurate to say that he's ignoring it rather than avoiding it.

Wouldn't you just turn your gaze away as if you were looking at something dirty or annoying?

What, you're saying you're going to get away with it because I said something when I was going up to Hwagyeong?

Are you upset?

Then, it was a terrible sound that made millions of eyelids close.

Qing was speechless.

That's really crooked.

But what's the big deal?

What was there that you regret?

The lamas of the Blood Thunder Temple were outside the mountain gate, listening and giggling.

However, if someone sees you, they'll probably scold you for being giggly right now.

At night, the smelly men would huddle together under a blanket, and only manage to get some sleep during the warmest part of the day.

Countless days of having to endure chewing on raw, tasteless barley flour.

Even rice, rice was not enough.

Because the Kunlun faction was late, they didn't have enough food to eat, so they ended up eating only one meal a day and surviving on nothing but hunger and thirst.

So, the lamas were also filled with evil, and they were very murderous, saying that they would kill all of these lazy bastards, these dogs of Kunlun.

But if we really have to be picky, it was self-inflicted.

The reason the Kunlun faction was late was because they judged that all the small villages and tent villages had been annihilated, so they delayed their mobilization to provide supplies.

Anyway.

The lamas, including Runrin, were listening intently to the sounds coming from inside the Blood Thunder Temple.

And those sounds were usually screams, wailing, maniacal laughter, and things like, "We're screwed now."

So, the lamas were preparing to kill anyone who might escape (unintentionally) with a mean smile, relieving even a little of their burning hatred.

Because there was a most ignorant way to escape the formation.

It's just grabbing the person and throwing them outside.

If you walk on your own, your five senses will become distorted and you will not be able to walk straight, and you will just end up going around in circles.

There was no way to lead someone out, so from the perspective of someone following behind, this person would sink to the ground, then rise into the sky, then appear from behind, and move in a myriad of ways, right, left, and back, making it impossible to keep up.

But what if you throw it away?

It feels like you're going through the ground, going through the world, spinning around, falling, flying, and crashing down, which was very harmful to your heart, but the trajectory itself doesn't change, so you're successfully thrown outside the formation.

Of course, there was no guarantee that a person affected by the formation will throw in the right direction.

But if you just keep throwing it away, someone might escape and ask for help from outside.

So the role of the lamas was to block the rear where the Kunlun warriors can fly in.

The Emperor of the Giant Pagoda had promised not to completely destroy the Kunlun sect but to leave some behind to give them a chance to see blood, so the lama monk stood guard and waited for him, burning with resentment.

What kind of expressions would the Kunlun faction's Malko have when they saw themselves, having been defeated and fled without even knowing that they had been let go?

And I sadistically imagine how I should kill them so that I can feel satisfied that I killed them well.

That was the moment.

Suddenly, the world becomes dark as if thick dark clouds have blocked the sun.

But it was a land of the Blue Sea where rain and snow were rare.

Besides, where on earth did those clouds come from in the sky that was clear until just a moment ago and made it dark?

The lamas raised their heads at him.

The crimson sun begins to open its eyes, and meets the eyes of the world's most unclean evil star.

The material of Manra Daehyeolmyeolcheonjin was a core that receives the image of a malevolent spirit and spreads it throughout the world.

And three thousand hearts, three thousand brains, three thousand internal organs, blood, bones and flesh were needed.

Cheonsalgoseong was a sinister planet created by the condensation of evil from the three thousand worlds.

It was a ritual that borrows the power of the Great Evil Star that spreads light to a billion worlds.

Even so, the materials needed to spread this on the weakest scale, at the minimum, were three thousand human appendages.

But here, the one who holds a thousand years within him stands at the center.

In reality, it was not possible for an individual to possess that evil nature, but witchcraft was originally a manifestation that appears when many people speak and believe in it.

And the world calls this the child born with a thousand years of life, the murderer who was swayed by a thousand years of life.

The master of a thousand years.

The formation was distorted and expanded.

Rather than an expansion, it was a transformation into a hollow, thick-rimmed shape extending around the blood-stained sac.

And in that area, not the Kunlun School's martial artists, but the Blood Thunder Yin Temple's lamas took up residence.

However, the current owner of the thousand-year-old family had a unique hometown.

The modern people of Qing origin were inferior in every way compared to this ancient primitive Zhongyuan.

First of all, they have the same intelligence, just less wisdom.

However, his physical abilities were extremely inferior.

On the other hand, isn't it true that we lack the knowledge necessary for survival and only know how to handle the conveniences of civilization? In reality, isn't this the result of repeated degeneration as a species?

There was only one thing that modern people have an advantage over.

It was an imagination that continued to expand.

It was an imagination expanded through all kinds of media.

It was on a whole other level than the poor imagination of Zhongyuan people, which consisted of only the horrific and unclean images, blood, bones, internal organs, and parasites.

The sky was black, revealing complete emptiness.

On the earth, a sea of cold, dull molten iron rises and boils.

In the vast expanse of open space, without even a small hill, there was only a gray horizon.

Above the dark world, there was only one celestial body, a huge malevolent star that swirls and rotates in every color that exists in the world, but not one of them was an ominous color that exists in the world.

Inside the veil, a huge, swirling typhoon of color slowly lifts its closed eyelids.

A huge hole between the whites of the eyes, staring at the endless abyss of the Lama.

It was a completely different world that no one in the world could have even imagined.
