\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (8)}

Today, Qing stops by the guest room's performance hall.

If it's a well-established martial arts school, it's customary to create a separate training room in the guest room.

Of course, not all guests, but the level of the guests must be high.

Just as the Half Sword Swords Club freely uses the training room of Mucheon-gak, the highest-ranking guest house in the Wulin Alliance, as if it were their own.

It's already been a while since Xue-i-ri got stuck. Um, I don't know how long it's been.

Since Qing was in the Repentance Hall, there was no way to know when Xue-i-ri was locked up.

After leaving the Repentance Hall, I only heard rumors that they were doing something inside and that they had gone in with a wall-mounted camera.

Still, in the evening, he knocked on the door and called out.

Of course, training was good, but isn't it all about making a living?

Besides, Gunyeong was of such a lowly level that he could be called a warrior, but he doesn't show his face as if something was unusual.

The only thing I like about him was his face, but if he doesn't show his face, what's the point of his existence?

So, it was a request to call her once a day to go out for a meal.

Knock, knock, knock, knock.

"Gunyeong, wouldn't you like to have dinner with me? Let's come out and eat together. I can't stand seeing your face. Why don't you come out?"

That's what I'm saying, but I don't really have high expectations.

Have you ever experienced the cold for a day or two?

Because this vicious girl Gunyeong was really determined to gather deceit once she starts to properly accumulate.

Qing listens outside the training center.

At this point, you can hear someone from inside saying, "It's not a hole." and then replying, "It's okay."

Then, I say goodbye and go back out to eat. That's it.

Actually, it's just something to do before eating, but it's not like the food doesn't taste good if you don't have any seol-i-ri.

The food at Kunlun Pao was also really delicious.

I wonder what will come out today.

It was at that time that Qing was smiling brightly, swallowing his saliva and licking his lips.

But? Why? No answer?

What the heck, were you sleeping?

I thought you were studying hard because you were so focused on it, but you're just pretending to study?

Somehow, it's convincing.

"Hey, Gunyeong? Let's eat. Huh?"

But there was no answer.

What? Are you rebelling? Why aren't you answering?

I'm not a parent who has to run around and pack food and feed my daughter, who was preparing for the college entrance exam.

Now that I think about it, taking an exam was ultimately something you do for your own good, so I don't know why your parents have to be concerned about what you think, but, Hmm, I guess I was an unfilial son.

Qing knocks on the door one last time.

Even if you happen to be dozing off, the sound effects were enough to wake you up with a start.

But there was no answer.

Qing was qualified to be called an ecology expert or authority.

Even though she was sullen and irritated, she never missed an answer, so at this point, you could tell that something was wrong.

"Hello? I'm coming in?"

But just in case, I'll give you a warning.

And then he pulled the door to the training room.

Squeak, tink, tink, tink.

Unlike the doors of the repentance hall, which open and close without making a sound, the doors of the practice room open with a loud noise.

It's not that it's not managed, it's that it was designed that way on purpose, and it's the same for any training room.

Of course, if someone sneaks in during the training, something big could happen.

As soon as you open it, it feels like you've opened a freezer, and the harsh cold air escapes in the form of white smoke.

Did he leave the window open?

Usually, there aren't windows in the training room?

Then, there was a woman lying in the middle.

Rather than just lying down, wouldn't she be naked and revealing her pure white body?

omg!

Qing runs in hastily, gasping for breath.

Looking closely, it was an even more gruesome sight, with his lower body completely dyed crimson with blood, and his nose bleeding and even vomited blood.

Moreover, his body was as cold as ice, so Qing quickly took his breath and pulse.

The breathing was deep and even, without any interruptions, and the pulse was strong and beats well.

In the doctor's opinion, um. Very healthy?

Somehow, his expression was so calm that he seemed to be smiling like Buddha.

I thought this was a sign of a good night's sleep.

What the heck? Why was this woman laughing?

Found smiling in the Xue-i-ri training room?

What do you do to be lying naked, covered in blood, and laughing while sleeping?

Qing first closes the door to the training room.

But I'm still scared of who would see my beautiful wife naked.

Then he grabbed Xue-i-ri's bangs and shook them thoroughly.

It's a bit of an extreme method, but once Xue-i falls asleep, she never tries to wake up.

You could tap the cheek, but then you'd get bloody.

"Hey, come here? Should I at least cover myself with a blanket and go to sleep? Are you going to catch a cold again?"

Now that I think about it, I think he really sleeps well no matter what.

Wouldn't you rather sleep in a cold water canal?

"Ugh… Miss Ximen?"

As I shake it like that, Xue-i opens her eyes.

And then, upon seeing Qing, wouldn't he give a yeomantic smile that was half joy, half affection, and half relief, and that was about five times more intense than usual?

Qing's heart sinks.

It's a truly heart-piercing, harmful smile.

It was a rare sight to see the snowy landscape, so it was a shame that there were no cameras in the central region.

Miss, I need to take a picture of this and keep it.

According to the observation results of Xue-i-ri, he had a hard time coming to his senses even after waking up, whether it was due to low blood pressure or just a characteristic.

Usually, didn't you just look at Qing with half-open eyes and say, "Please do it?"

I have to wash them, dress them, and feed them breakfast before they come to their senses.

But you laughed? What kind of structure was that?

Which button should I press to put a smile on my face?

What did I do? Or was it environmental factors?

Do you laugh when you wake up naked?

Or by grabbing your bangs and shaking them?

It was the moment when Qing was analyzing the difference between her usual mood and her smiling mood.

Xue-i-ri whispers in her usual, yet somehow excited voice to Qing-i's ears.

"I'm at my peak now."

"Oh my. How can this be? A climax?"

As Xue-i-ri's eyes widened even further-

Qing was the type of person who cannot appreciate pretty and cute things.

"You're saying she's at her peak now? Gunyeong, you don't usually boast about being at her peak at that age. She's twenty-three, no, she's one year older. And now she's at her peak at twenty-four? Oh my, my child was so lacking."

At that, Xue-i-ri's eyes straighten.

It's a shame that the smile has disappeared, but I guess I have to say what I have to say.

"Normally, you wouldn't brag about something you can do, right? What's the difference between that and someone in their twenties saying, "I can use chopsticks now." Can I even walk now? It's embarrassing that I used to crawl."

"No. It's different. No."

"So what were you doing naked? You seem to be the type to practice while completely naked, but Gunyeong was the type to strip completely naked and practice. Yeah, I get that feeling. It's definitely more comfortable to not have anything on."

"No, no. No. No."

His eyes scanned Xue-ri's naked body and-

"Well, it looks nice. But first, let's put on some clothes. I'm afraid someone might see."

Congratulations! Xue-i-ri has reached her peak!

Heemae was completely confined in the training center, a confinement training center, so there was nothing she could do. Upon hearing this surprising news, Pang Daesan's feelings were as follows.

"That's a stupid way to do it. Was there a reason to go that far?"

"What kind of ignorant method was that?"

"It's a technique used a long time ago. I heard it was practiced with extreme caution, with a master and elixir, as it could easily lead to ruin. It must have been so dangerous that it was called the "gateway of life and death."

"Oh? Here you go?"

Qing looks at Xue-i with a sense of rebuke.

Of course, I intentionally bullied him more to raise his level, but it wasn't a joke that made him risk his life.

Although the battle at Qingdo was desperate, the life-or-death battle ultimately relied on the might of the general.

At least, wasn't it after you had made a way for yourself to survive?

But Xue-i shakes her head.

"No. That's how the North Sea is."

However, according to Xue-i-ri's explanation, the forced passage of the Imdok Yangmaek was originally a long-standing tradition in the North Sea.

Well, so you're saying that the North Sea was so primitive that even challenging it was undeveloped?

Of course not.

This was a unique feature of the martial art called Bingbaek Shingong.

The Ice Han Ji Jeong planted in the Danjeon itself was a divine being that transcends the providence of the human world.

So, if you just connect the Imdokyang vein and connect it, you will be transformed by completing the Great Circulation.

The body was optimized to match the ice crystal through a complete transformation, so it was said to be at the peak of its power.

It was usually said to be the opposite order of the current method, in which the Imdokyang vein was opened through transcending oneself through enlightenment and optimizing one's transformation.

Anyway, with Xue-i-ri as the last, all the members of the Half-Geom Ssangdohoe climbed to the top of the ladder.

Jegal was not a combat agent, but rather a commentator and explanation agent, and Nan-ah was a medical support and poison spray agent, so they can be said to be unmanned.

Changbin does have a child, but he was a member of the pants club, a ghost member, and an inactive honorary member, so that's not the case.

Someone passed by and glanced at Qing party's hearty meal (albeit with a bit of overeating).

When he entered the long gate, Tian Feizi bowed and greeted him.

He was bent in half at the waist, his crown almost touching the ground, so it was easy to see why the expression "bowing" came to be.

"Oh my, Senior! You must have had a hard time coming this far. Aren't you tired?"

But the picture was a little strange.

He was a Kunlun sect leader who looks like a ninety-year-old man, as he was a thousand-year-old man with wrinkles that were unusually thick for his age.

In comparison, the man who was greeted as a senior was still a man, with fair skin and the appearance of a young man in his thirties.

"What hard time? What could be tiring when a middle-aged man walking around? So what's the big deal that you're calling all the old men who should been meditating?"

A young master wearing a red-and-yellow Shaolin robe naturally responds with condescension.

It may seem strange to others, but in reality, there was nothing strange about it.

Because that man was Wunue.

The number one master among the Ten Greatest Masters Under the Heaven.

"That's-"

Just as Tian Feizi was about to begin her explanation.

"Ah. Right. I saw that Heavenly Blossom Sword child on my way here. I already heard she'd ascended to Unrestrained Realm, isn't this truly astonishing? It seems Ximen Zhenren is here too, but she deliberately avoided seeing me. She pretended not teaching her disciple, yet at the same time she's bragging about it. Isn't that child from North Sea also reached Transcendent Realm? Seeing someone of Orthodox faction with a bright future is satisfying, but at the same time, I'm sensing a crisis. This is a very serious matter."

"Huh? What are you talking about all of a sudden?"

"Listen. Look at the friends that Heavenly Blossom Sword often hang out with. Nan-Gong, Murong, Peng, their children were all said to have reached Transcendent Realm, and now even the North Sea child has followed suit. How can that be reasonable at that age?"

"Isn't that a wonderful thing? They must have been inspired by Heavenly Blossom Sword, who had reached the Unrestrained Realm. And since they were hanging out with peers, they developed a competitive spirit and trained fiercely, which was probably resulted like this."

"That's the problem. Why does she only hang out with the kids from the Noble Family? How about that crybaby of yours? Excluding my bald brat, how many kids in the Nine Sects are at the Transcendent Realm?"

Only then does Tian Feizi's expression become serious.

Of course, even if they were on the same rank in the Wulin Alliance, wouldn't the Nine Sects (plus one Union) in the Wulin Alliance be considered one level higher than the Five (plus five) Noble Families?

But look at the youngsters of Ten Noble Families.

Sword Lunatic, Jade Qilin, Sword Flower, and Xianyuan Sword.

Of course, the center was Heavenly Blossom Sword, and she was affiliated with the Divine Maiden Sect (though not strictly speaking).

"But, isn't it something that can't be forced?"

"What else can be done? When young children band together and roam around in groups, friendships form, right? Are close friends always close from beginning? They're all grown men now, past twenty. Aren't they just too attached to their sects? So wouldn't it be nice to have them by Heavenly Blossom Sword's side, even if it's just half as much?"

The so-called Half-Sword Double-Saber Association membership quota system!

How about having one disciple selected from each of the Nine Sects to join and mingle?

The expression on Monk Wunue's face as he spoke was completely serious, with no trace of joke.

In fact, the rivalry that exists between the old and new factions has been well known since ancient times.

It might jokingly called rivalry, but in the past when Jianghu was much more difficult than it was now, there were conflicts that could be called strifes.

Anyway, the reputation of the Half-Sword Double-Saber Association was growing rapidly.

So, in the future, more people will come to understand the true meaning of the Half-Sword Double-Saber Association and the profound implications hidden in its name!