\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (7)}

Ximen Surin's was an early riser.

While the sky was still dark, he wakes up, meditates quietly, clears his mind, adjusts his clothing, burns incense on the altar, and prays for the well-being of his disciples and monks.

Then, he sits cross-legged in the main hall, practicing qigong, and waits for the morning greetings of his disciples.

She waited for her disciples in a neat posture without a single strand of hair out of place.

I wonder what the disciples will think when the old master lets go because he was old.

That's how you start a long day.

It was a very long day.

The disciples were now older and each has their own sect's work to do.

So, since not everyone can come to say hello every day, we take turns showing our faces, but that's it.

When I go back in the morning after seeing their faces, everyone was busy with work and teaching their students.

Then, since I have plenty of time, I have no choice but to meditate and study the sutras to find clues to enlightenment, swing my sword, and practice the Dharma, devoting myself to training.

It was said that when the young disciple who came in at the end of his days stayed, the days were not this long.

From the morning, the now-grown-up girl would smile brightly and innocently, and wouldn't she show her face to the teacher, unaware of his fear?

No matter how much you scold him, he has a unique, long stride that doesn't change, and he walks with a very frivolous gait, laughing childishly.

So I start my day with nagging that has almost become a greeting.

If you cultivate yourself through dialogue and dialogue, it will be lunch before you even swing a few times, and dinner before you even exchange a few words.

But the strange disciple soon wanders outside, and the day becomes endlessly long.

Anyway.

Habits that have been ingrained for a long time rarely change.

That was why Ximen Surin's mind naturally woke up even though it was still dark in the early morning.

Usually, I just lie down and meditate until my mind was clear and clear.

however?

The coldness that weighs down on the body,

Something like a soft thread tickling the corners of the mouth.

The sound of snoring, softly, right next to my ears.

Ximen Surin's eyes widened.

What you see was an unfamiliar ceiling.

When I raised my head, all I could see was shiny, jet-black hair and a particularly white, transparent nape of my neck that stood out between them.

The poor disciple shamelessly covered her master's body with her own, crushing him, and snoring loudly in his ear.

Ximen Surin was speechless.

Regardless of whether it's a man or a woman, people don't usually sleep with their bodies on top of each other.

Because it's uncomfortable.

It might be understandable for a three-year-old child, but that was the reason why he didn't climb on top of people to sleep when there was a soft, round bed.

Surprisingly, the human body was hard, and there were bones under the skin, so if you put weight on it, it will get stuck here and there.

Rather, it was said to be brave, or perhaps even great.

But surprise was surprise, and for a poor disciple to be so reckless, there must be a price to pay.

So Ximen Surin clenched his fist.

A twelve-level fission reactor has been detected.

Warning. Warning. Nuclear launch detected.

And then-

The thermonuclear fist that was about to be ejected stopped.

Suddenly, a flash of memory flashed through Ximen Surin's mind, halting his advance toward the magnificent destruction.

"Master? Are you going to sleep already? I prepared water for you to wash your face. You should wash your face."

"It's so cold I haven't even shed a single drop of sweat, so what's the point of washing my face? Besides, I've never missed a day of it in my life, so why bother taking a day off? Isn't it just a hassle?"

"Hey, but you'll feel better after washing your face, right? Then, I'll do the washing for you today."

And then, the warm towel gently tickled my warmed skin, the fragrant scent of incense (soap) wafted into my nose, and the sound of water splashing seemed somehow pleasant.

"Okay, Master, hmph! If the water in the wall doesn't drain, it'll be hot."

At this point, Ximen Surin's expression on the bed suddenly turns bright red with extreme embarrassment.

What kind of old man with dementia was he being cared for by his granddaughter?

And then I lay down peacefully and enjoyed the feeling of my disciple gently pulling my scalp with a towel as he gently combed my hair.

'Master, then, I will step down as a disciple.'

"You, how can you so cruelly abandon your teacher?"

Then he hugged me tightly, pulled me in, and held me tightly.

Yes! Qing was innocent!

That damn alcohol, alcohol was the problem.

Maybe it was because I had been drinking too much for the first time in a while, or maybe I was just drunk on the excitement of the Lunar New Year night market.

Perhaps because he was a strict and dignified teacher, he brought out and revealed a side of himself that he had always kept hidden.

The teacher, who was now quite old, has given birth to a child. How will he ever see his disciple's face again, and what will the disciple think of him?

It was a dawn when my legs were itchy and I felt the urge to swing them.

That was when.

"Um, uh, what time was it…?"

Qing, who has a cheerful personality but was sensitive to sounds, speaks in a voice that was still not fully awake.

And then he makes a sound like, "Oh, oh," and supports the body that was crushing his master with both arms.

With a head space between them, the face of a beautiful disciple fills my field of vision.

So the whole world was the face of the disciple.

And wouldn't the world be filled with happy smiles?

Ximen Surin stared blankly, not even realizing that her mouth was open, as if she was in a trance, looking at the most precious thing in the world.

The disciple was lying face down with his arms resting on his master's shoulders.

Qing chirps softly in her characteristically beautiful voice.

"Master, have you been coughing?"

The son-in-law was in the dark, but neither the master nor the disciple was bound by that degree.

Ximen Surin was a master who has reached the state of Hyeon-gyeong, and Qing was originally a night vision expert who has superhuman abilities.

"Ahem, how could you possibly be doing that?"

Then the impudent disciple fell to the side, but then clung to him again.

He shamelessly hugged his teacher's waist and even pressed his cheek against his.

"Hey, how can you lie down again?"

"Well, it's still midnight, and the sun was still a long way from rising. Isn't enjoying the afterglow of a little sleep in the dark the very joy of life?"

And yet, the gaze that touches my cheek feels tingly, so even without seeing it with my eyes, I can clearly see the affection and affection shining through it.

I feel a great sense of relief, pretending that I am not Ximen Surin.

Then, suddenly, last night, he would not have looked down on or looked down on his teacher, saying, "It was so embarrassing."

Of course, Qing was a disciple who had been close to his master since long ago and did not know at all how difficult it was for him to be a master.

This was precisely why the origin of man was like this.

But would the other disciples be like that?

Even if the teacher was strict and difficult in order to set an example, the disciples will not be indulgent or dislike the teacher if he does not do so.

This was because it was a solid foundation that has been solidified by the accumulated time up to now.

Is it really against human nature to appear drunk?

But if it has been solidified over a long period of time in a form that has taken shape for a specific purpose, can such an embarrassment change perception?

If it was not a person but a sword,

The nature that people originally want to wield.

The nature of a sword was to take form, and when seen by others, Hmm.

Unorganized questions swirl around in my head.

Of course, even if you become a master of the realm of the supernatural, you don't suddenly reach enlightenment like those who were far from the peak.

It was not a question of depth of enlightenment, but rather a question of embodiment and experience.

Martial arts were something that develops over a long period of time and contains its own mysteries. If you properly understand and internalize the experiences and secrets that you have learned and practiced without even knowing it, you can quickly reach a higher level.

No matter how outstanding the ancient martial arts were, the level of the ancients did not surpass the level of martial arts today.

Even the absolute rulers of the past were already considered the best in the world at the time, like Hwagyeong.

By the time you reach Hyeon-gyeong, you have already reached a higher level of enlightenment than the founder of martial arts.

So, when we talk about martial arts in Hyeon-gyeong, we mean pioneers and forerunners who were expanding the entire field of study called martial arts, its foundation itself.

How could it be so easy to seek enlightenment that never existed in the world?

So, just grasping that topic was a huge turning point.

Wouldn't it be better to slowly chew on it and sharpen it like sharpening a knife?

Gororong. A cute sound tickles my ears.

In that brief moment, the disciple fell asleep.

Ximen Surin slips out of bed and opens the blanket over Qing.

Without realizing it, the corners of my mouth curved gently.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Xue-i Lee literally went through hellish training, spending ten days in Kunlun Mountain, just praying.

He would even stack up jars of water and a wall of rice cakes next to him, take them out one by one whenever he felt hungry, drink water when he was thirsty, and even replace sleep with luck, concentrating solely on accumulating the internal energy he lacked.

It was truly ten days of celebration.

And then at some point.

Xue-i-ri intuitively felt that the time for decision had come.

So there was a faint furrow between the eyebrows.

If Qing had seen it, he would have interpreted it as a very focused expression.

In Xue-i-ri's still insignificant dantian, true energy gathers around the iceberg and forms a large mass.

A trivial miracle that came together like that.

And then all of a sudden, all of the energy was released at once, and the speed was as incredible as a fired shell.

This was shooting out internal energy at a speed that even one cannot control.

If you were to list the taboos that unmanned people should not do, this would definitely be included.

If you just shoot out your true energy like this, the true energy will lose control and run wild inside your body, tearing apart your blood vessels and energy channels.

It was a dangerous act that could end well as a minor injury, and in the worst case scenario, it could even shatter the dantian.

But why?

In fact, this was one of the life-threatening training methods used by primitive ancient warriors.

The energy that was gushing out powerfully passed through the perineum and reached the back of the spine, passing through the beautiful, famous, and middle parts of the spine, the sacred pillars, the jujubes, and the jade needles, and rushed towards the crown of the head, towards the tightly blocked wall above the upper abdomen without losing speed.

bang!!!

Xue-i-ri's back bent like a bow.

Blood gushed out of both nostrils with a force approaching spurt! Unable to untangle his legs from the entangled lotus position, he lay on the floor, convulsing in large and small convulsions like an epileptic.

"Ugh, ugh. Gasp, huh, ugh."

The pitiful sound of trying to force air into the lungs keeps leaking out.

I kept fumbling around like that for a while.

Xue-i-ri raises her upper body again and wipes the area under my nose.

Because of that, it ended up becoming a bigger mess because it spread.

Hoohoo, Xue-i-ri takes another deep breath and gathers her inner strength again.

The internal energy that had gathered again went wild and was forcibly ejected, the energy that had been shot gathered and fired again along the poison meridian at the back of the spine, bang!!!

Xue-i-ri's back bent like a bow again.

With a scream of "Keu-guk!", he vomited bright red blood from his nose and mouth at the same time.

He was lying on the floor, gasping for breath and panting, but somehow the corners of his mouth were turned up into a smile, so anyone who saw him would suspect he was possessed by an evil spirit.

But Xue-i-ri's expression was bright.

Before I knew it, the blood vessels had burst and the whites of my eyes were turning red, but what was so good about it?

Well, my head was cracked and about to fall apart.

This does not refer to the function of the skull or brain, but rather to the thick barrier that blocks the largest blood vessels in the body, the Ren and Du vessels.

Even as her nose continued to bleed, her eyes were streaming with faint red tears, and her mouth was parched with the stench of iron, Xue-i-ri got up again.

The energy along the spleen was torn and tattered, causing terrible pain.

The Du-maek was the most important passage through which energy flows from the Dan-jeon and was distributed throughout the body, so if this part was damaged, fatal aftereffects will follow for the martial artist.

But Xue-i-ri doesn't care.

So one more time.

Ready, shoot!

At that moment, a bolt of lightning strikes Xue-i-ri's head.

As the blockages were shattered, an indescribable sense of refreshment fills my head.

I had to cover my mouth to hold back the sounds that were about to burst out without me knowing.

Shoooooooo-

A pure white cold energy was released from Xue-i-ri's entire body.

The frost was so thick that it covered my entire body, and my clothes were so frozen that they were completely shattered and crumbled.

The cold air fills the training room, and a white frost forms on the floor, walls, and ceiling.

Among them, Xue-i-ri feels some powerful, fundamental flow that restores her body, a powerful life force that she doesn't know where it came from, filling all her blood vessels and the eight meridians.

A strange, yet not unpleasant, feeling as if your bones were tickling, your muscles were cramping, and your skin was writhing about.

It was a feeling of complete transformation.

This was the forced connection of the Imdok Yangmaek!

It was a primitive and extreme vision of the primitive ancient martial arts world that was forced to reach its peak.

The attempt itself was dangerous, and inevitably the poison vein was damaged during the process, and the true energy and the true source were damaged?

However, if successful, not only will you recover completely, your body will be reborn and optimized for martial arts.

There, Jin-gi and Jin-won-jin-gi return to something even more enormous.

In the hometown of Qing, this kind of match was expressed like this.

Just pay it later!