\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (3)}

First of all, that candidate, first.

A Midsummer Night's Dream ending.

Of course, it's not midsummer, but midwinter.

The plan was to finish the five-day tour of Repentance Hall and quietly disappear into the night.

Baekmi woke up in the morning and felt a sense of emptiness as she realized that the summer was gone and nowhere to be seen.

And I asked the single-minded Zhenren to take responsibility for the fact that one of you has escaped from prison.

Two meals a day until the end of the Lunar New Year.

Know that there will be no lunch, no dinner. Not eating dinner was intermittent fasting, and it's good for your health, so it's like giving the sick one another another beating to be thankful.

It was truly a midwinter night's dream.

But it was summer… 

However, it had the disadvantage of being very boring and difficult to observe the reactions of those left behind.

Even if I try, I can only eavesdrop on the sounds behind the wall of the repentance hall, but it's a bit awkward if I can't see that desolate expression with my own eyes.

Above all, you have to put up with some of the nuisance.

Wouldn't this instill in the prisoners the belief that the prison was not an impenetrable fortress from which escape was absolutely impossible?

Then the prisoners will be on the lookout for an opportunity to do something stupid.

Even if that weren't the case, the prisoners who should be rotting away helplessly shouldn't be given any energy.

So, the disappearance of Da-yeoreum was rejected.

Candidate number two.

The ending of playing Friends was fun.

But I don't want to be friends with these guys even for a little while.

Well, what should I say?

Do you know the topic, you idiots?

Anyway, the second option.

He reveals his true identity honestly and takes charge of the management of the repentance center for a day or so, and lets him have fun leisurely.

It's not Madu Da-yeoreum, but the young master who rewrote the history of martial arts, no, it's Seo Moon-Qing who appears as the only young master in the history of martial arts.

It felt like I could just play around with it all day.

Your martial arts were sold cheaply for a few dishes.

Now this martial art was mine.

It can be stored in Janggyeonggak.

I could buy a bunch of Lunar New Year snacks and spend the whole day munching on them and explaining their flavors to you bastards.

But the second one was also rejected.

In the future, there may be people who come to experience the same thing as me.

Aren't these demons who have been trained over a long period of time to regard the Repentance Hall as their own grave from which escape was impossible?

Thanks to this, I was a newbie who was treated with suspicious favoritism, but I was so ignorant that I didn't dare to doubt him.

What if I reveal my identity and set a precedent at a time like this?

Because it would be a great hindrance to future generations who come to experience the Repentance Hall.

The third candidate.

Even the Kunlun Taoist priest, you have an ending.

The summer of the annihilation of the King of Organs and the God of the Organs was the strongest in terms of connections.

It was a summer that even the hardened heart of the Kunlun Taoist priest was opened wide, so he leisurely escaped by mocking the prisoners of the Repentance Hall with the Kunlun sect's traitor!

"How was it? Isn't it okay?"

At that, the single-minded Zhenren raises his eyebrows.

Qing sneaks out during the night, takes a bath, eats a late-night snack, and comes back.

The prisoners, who have lost their dantian and become numb to stimulation, cannot even sneak out while they were sleeping?

The next Shinto qualification should just be thrown away.

Danlun Zhenren responded to Qing's absurd suggestion as if there was no need to think about it.

"Why on earth? Are you going to do it in the morning?"

Wasn't it the Danlun Zhenren who volunteered to be on duty at Repentance Hall, saying it would be fun?

In fact, it was a trick to escape from the endless herbal medicine boiling under the pretext of taking care of the Kunlun sect's precious guests and just spend the whole day reading books at the Repentance Hall guardhouse.

But this method could also cause major aftereffects.

First of all, the Danlun Zhenren might get caught up in unnecessary gossip, and later on, it would only be troublesome if the prisoners flirted with the Kunlun sect's Taoists.

Above all, it was giving useless hope to the prisoners in the repentance center. Wouldn't it be difficult for the prisoners who have to stay locked up with their eyes like rotten fish?

"I don't really mind."

It seems like Danlun Zhenren was quite excited.

Anyway, the third one was also rejected.

It was a sincere request to harass the wicked.

I thought about various ways to make the medicine more potent, how to make it more irritating, more exhausting, and more angry, and there were countless other things I came up with.

"How about this?"

Suddenly, the wall of the Repentance Hall collapses and a strange man riding a white horse appears and shouts.

'No time to explain, get on quickly!'

"You can't destroy the building."

"Well, since it's an empty prison anyway, wouldn't it be okay to cover it with a tent? The prisoners would probably be a little cold, though."

"Someone's going to work during the Lunar New Year. If you'll help me build it back, I'll try to get the white horse."

Even though it didn't seem like it, Danlun Zhenren secretly showed his enthusiasm.

Of course, if you want to build a wall, there's nothing you can't build, but let's see, it's a triple wall with three layers of bricks and thick insulation.

This.

Come to think of it, isn't Danlun Zhenren just barely at his peak?

It means that it was a sewer that was difficult to just break.

It's not something you can ask for a difficult task.

"You have a somewhat rude look in your eyes."

"Hey, no."

Since Qing's acting skills were only good in front of villains, he can see right through me what I'm thinking during normal times.

As Danlun Jin-in looks at Qing with narrowed eyes, Qing laughs and changes the subject.

"Where can I get some blood tomorrow? Oh, and aren't you going to slaughter a cow or pig tomorrow morning? The Lunar New Year banquet will still be going on, so I think they'll be slaughtering them."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Do you know the feeling of a soft morning?

The haziness that seemed to move between dreams and reality was washed away without regret, and consciousness gradually became clearer and one became naturally aware of one's own existence.

When I opened my eyes, it was a bluish morning.

Somehow, my mind feels refreshed, my body feels whole and free of any knots, and I begin to feel energized.

A truly refreshing morning.

Killer Demon lies down, intoxicated by the afterglow, and thinks.

How long has it been since I've had such a refreshing and wonderful morning?

Come to think of it, I haven't had a single full morning since I came to Repentance Hall.

Well, before he was caught, Killer Demon's power was not ordinary.

Killer Demon used to sleep in a luxurious bedroom like an emperor, lying on the world's softest silk, smoking expensive incense.

However, the beds in the confessional were hard and stick out like rags, and even then, they were not filled enough, so they were hard and the body feels uncomfortable.

The quilt was just sturdy, made of rough hemp cloth stuffed with cheap cotton, making it heavy.

The musty smell of never-before-seen clothes was a bonus.

Is that all?

It was hot and humid in the summer and cold and dry in the winter, so both the facilities and the weather were extremely uncomfortable in Repentance Hall.

That's not all there was to it.

These guys wake people up by ringing the bell from dawn, so they intentionally make it thick and noisy to the point of being unbearable by scratching at their nerves.

Killer Demon's eyes flashed open.

He thought it was a really refreshing morning, and then he realized why.

There's no morning bell!

The worst kind of wake-up call was when someone wakes you up and forces you to shake off the rest of your sleep, so this was the first time in decades that you'd woken up from a sound sleep without any disturbance.

But why?

Are those Kunlun faction bastards slacking off for the first time in a while because it's the Lunar New Year?

That was when.

"Oh, old man. The early bird gets the worm. Are you old and can't sleep in?"

The voice of a reckless bitch who doesn't want to be seen.

It was a time when Killer Demon pretended not to hear and ignored it.

"What? I know you're awake. Aren't you going to answer? Don't you want breakfast? Are you old and have no appetite?"

"…This old man just woke up."

His pride was hurt, but he wanted to eat the food.

But the breakfast that Qing was talking about wasn't about cooking.

"I was thinking of serving them in the order you wake up. This morning's special is a nutritious soup brimming with human blood. Didn't the old man say something about the fragrant aroma of human blood? Or did the cannibal bastard say that?"

And then boom.

Something large flew in front of Killer Demon's brain and fell down with a splash. It was a hat with a silver tube attached to its head.

It's an item usually worn by Taoist priests of Kunlun.

Killer Demon was startled and runs in, grabbing the iron bars.

He saw Qing sitting in front of a food cart at the entrance, covered in blood.

Killer Demon screams in shock.

"You, you!"

"It's time to eat breakfast. Wake up, everyone!"

Qing put the ladle between the bars and shook it from side to side, and the noise as loud as the sound of a bell shook the whole of Repentance Hall.

"Shit, what is it?" "Did they change the bell?" "Fuck you! Sleep! Let me sleep, you bastards! Please, just for one day!"

The cries poured out at the forced wake-up.

But these were Demonic Adepts that had been tamed for at least ten years, so they jumped up from their seats at the sound of metal clashing.

And then finally, they found Qing, leaning proudly against the food cart.

"What the hell is this-" "You, what!" "You did it!"

Exclamations of astonishment or exclamations.

Qing smiled at him and said-

"Here, look here. It's sparkling."

Purple light ripples and flashes above Qing's hand.

But because it was still a dimly lit place, the brilliance stood out even more.

"In fact, this Heavenly King of Apparatus Formation Cha Xiantian's dantian is still intact!"

The evidence was clear since she's already emitting strong energy.

Qing looked at the prisoners with their mouths wide open and made an evil smile.

"No, honestly, how can those so-called Demonic Adepts survive without even realizing it? You're so pathetic, uou're worse than beasts. If I were you, I'd just bite my tongue and kill myself, having lost my dantian and living a miserable existence in a place like a barn. Sigh, you truly vile bastards."

"What-"

"Look. I wasn't captured. Why was I brought here? Now, does anyone know what this is?"

Qing waved her right hand.

Behind the purple, strong hand, something white, twisted and shaped like a devil's grip, was translucently covering it.

"White Hand Witch! You, you're the Witch of the current generation!"

Killer Demon screams at Barak.

"A witch? No."

This time, Qing swings his left hand.

A similarly twisted figure, but this time a pitch-black hand will not cover it.

"Black Slaying Demonic Palm! It's Black Palm! But your hand, how could it be? Black Slaying Demonic Palm came from White Hand Demonic Arts, so it erased the side effects of Black Slaying Demonic Palm!"

"Oh, old man. You're smart."

Still, he seemed to have quite a bit of insight, having once been a master.

"Then what about this?"

It seemed as if thorns were sprouting from Qing's body and spinning around fiercely, and at the same time, purple lightning shot out in all directions.

"Purple Lightning Demonic Arts combined with Samsara Demonic Tribulation, you bitch, how many of the Ten Great Demonic Arts Under Heaven did you have? Huh, I see, you bitch, this old man's Drunken Madness Killing Force were definitely your goal!"

"Correct. I was determined to unite the Ten Great Demonic Arts Under Heaven, but I heard that Killer Demon, this piece of trash, was locked up here. So, what can I do? I made a gamble."

"Hahaha! You're a completely crazy bitch! You were caught on purpose to get Demonic Art?"

Killer Demon looked genuinely amused.

Why would Qing just sit back and watch that happen?

"Yeah. But I thought Drunken Madness Killing Force is a strong qigong, but it's  burning lifespan? It's useless. I just wasted my time."

"What, what!?"

"So I thought, if I don't need it, wouldn't it be better to just break it?"

"You bitch-"

"So, the Drunken Madness Killing Force lineage ends here. When I return into Jianghu, I'll just say I didn't learn it because it's a third-rate martial art, consumed by murderous intent, burning lifespan and unleashing powers beyond my reach. Killer Demon was, in fact, just a madman possessed by a demon."

It was a declaration that your entire life would be denied and rendered meaningless.

Despite his terrible deeds, Killer Demon was also a great warrior who reached the heights of power.

But what if it's as Qing said?

From now on, I will just be remembered as a crazy person who was drunk on murder.

I thought he was a murderous spirit who was addicted to killing people, even burning his own roots, but it turned out he was just fooling me with his martial arts skills.

Killer Demon's expression becomes distorted.

Half angry.

And the trembling eyes were evidence of fear.

\textit{Yeah, this is it.}

\textit{It's so thrilling even without killing, I can't believe I lived until now without knowing that there was something this fun.}

\textit{Haven't you lost half your life in the martial arts world?}

Qing was excited, excited, excited, excited, and he automatically starts humming.