\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (2)}

Qing gave nicknames to each of the prisoners in the prison.

Poisonous horse, adulterous horse, dumpling ear, old man, etc.

But as I listened, I realized that it just seemed to stick in my mouth.

Originally, the prisoners in Repentance Hall also had their own surnames and pretended to have a hierarchy, calling themselves Wang Hyung, Jang A-woo, and Woo Sunbaenim.

Qing thought it was really a waste of money, so he gave it a nickname and spoke informally to it, pretending not to care.

So what happens?

A newbie, a young girl who looked like she was still young, came in and started talking to me informally.

As for courtesy, it was impossible to find out whether he ate the rice thoroughly or not.

Then a thought occurred to me.

Do I also need to be polite?

Anyway, I'm stuck like a cripple, it's the same.

On that topic, you're calling me older than you, but even if you did, you'd probably just die of old age here.

Senior, you said you entered the martial arts world more than ten years ago?

Anyway, was there any reason to respect something that was caught ten years ago after being a fuss about it?

I felt this deep sense of skepticism.

From the beginning, they only had a little bit of appearance on the outside, but inside they thought each other were idiots.

It took less than a day for the character to change from 'Hyung Jang' to 'Hey, you bastard'.

But the act of letting go of words was also the act of letting go of the heart.

If you were friendly by nature and know how to respect and love others from the heart, you will be able to easily open up about your feelings after speaking, and this will become a bridge that will lead to a friendship that was second to none in the world.

But what if it's the other way around?

What if you were looking down on him and thinking, 'At least I'm better than that idiot?'

The moment they let go of the words, the relationship was like a horseless carriage rolling towards a cliff.

Speaking informally was a way of subtly revealing one's true feelings.

In the end, the future was set to be one where the relationship was so bad that they become mortal enemies.

What kind of people were the demons of Repentance Hall?

To me, they were selfish people who didn't want to suffer even the slightest loss, and who prioritized their own well-being over the starvation of others.

So what about our relationship going forward?

In short, Qing poisoned the Repentance Hall.

And what does the poisoned Qing do?

It's already the fourth day in Repentance Hall.

Excluding the first day, Qing had a very enjoyable time during the three days.

Of course, the prisoners of Repentance Hall were like docile lambs and learned to live quietly, so wouldn't they be happy?

It can't be anything but amusing to see the big bosses who once turned the world upside down now obediently following orders while keeping an eye on things.

Well, the price that Qing offered was too tempting.

Wouldn't you say you'd choose one escapee companion who might or might not be used as bait?

Of course, the prisoners in the repentance center thought that this bitch would definitely throw this out as bait, but still, isn't this a once-in-a-lifetime opportunity?

Besides, this girl was somehow trustworthy.

Whether there was a supervisor or not, she was a woman who was very strict about giving and receiving, so even if she didn't get selected because she acted cute, wouldn't she still be able to get food?

So, the madhus also realized that if they could just let go of their pride, it was a business they could do without losing anything.

So from that day on, some people were busy trying to please others, pretending it wasn't happening, and some were even openly flirting.

Of course, that part was the most enjoyable for Qing.

Because these filthy little people have no self-respect left.

He has no conscience, no popularity, no dantian, his limbs and veins were cut off, and he doesn't even have a man.

Now that they have thrown away even the last bit of their pride, all that's left for these filthy creatures was a body that can't be used for anything.

If I leave it alive, I can eat and make fertilizer.

Now, even if you kill them, it would take more effort to clean them up, aren't they really defective products that don't even have an ounce of value?

When I think about it like that, a strange and strange pleasure wells up in me without me realizing it.

This was a new form of pleasure.

It can be fun enough without killing.

Perhaps immortality was the most powerful sanction available?

Batman, you were right.

If you forcibly keep them alive after making them completely disabled, it's not just a brief moment of burning pain, but it could also lead to them being stuck in a cesspool for the rest of their lives.

Is that all?

It can also stop the dull pleasure of killing and the hands that become increasingly cruel as a result.

I'm a Taoist after all, but honestly, if it weren't for the Divine Maiden Sect and my master, teacher, and friends, I would be okay writing a book about ten thousand ways to kill people.

But my reputation isn't just mine, so I have to be decent for everyone's sake.

Before, I was a lowly person who only knew the character ㅁ of martial arts or the character 武 of 止, so I didn't have the ability.

Now that I'm a proud master, I guess I have to save face.

Who am I? Hwa-kyung.

I too am now trying to maintain my dignity.

Even now, I just laugh at these bastards who have to watch their skins being skinned and salt sprinkled on them, or their necks being tied to a hot iron plate and their frantic dance of death until they die.

Hmm. But I really want to see someone dancing on a hot plate until their whole body was cooked.

If you meet a bastard who surpasses that bastard later on, well, there was one face that comes to mind.

Mr. or Mrs. Mo, or something like that.

Is there no way to get to the point of life and death quickly?

His usual gentle and elegant gestures were nowhere to be found, and he was acting very drowsy and trembling.

Wouldn't it be crushed and fall off every time our skin touches it? Wouldn't Nyong-ee also be crying and making a fuss, begging for her life?

It must be a truly extraordinary sight that you will never see again in this world.

But it's not like you can just go to someone's door and knock on it and tell them to open it right away or you'll break it down and get in.

All I can do right now was collect martial arts.

So now I was watching the squirming figure in front of the iron bars of the god of the outbreak, the guy who had his leg cut off during a daring escape attempt earlier.

The god of disease explained, swinging his arm around -

"So, here, if you flow the energy here to about three times, what was the acupuncture point here, on the elbow?"

"Gokjihyeol?"

"Ah! That's right. The Gokji point. First, you need to concentrate your energy by applying force to the Gokji point. Next, you need to direct it here, here, and here. You see here, here?"

"Onyuhyeol?"

"No, I don't think so."

"Extreme blood type?"

"Ah! That's right! The extreme! And in Susam-ri, they head out to the outskirts and rush towards Yanggok…"

The god of disease struggles and adds comments.

The god of the outbreak's occupation was a herb hunter.

As he climbed the cliffs, he picked the qi hua ying ch'o and gathered the stone qi, so all the precious elixirs that had settled in nature were in the hands of the god of the path.

The problem was that they covet not only the natural herbs but also those that other people have.

He claims that the ownerless object was simply picked up by someone who knew its true value.

The act of personally killing the owner and then taking it from someone else's house was called robbery in human terms.

So, I was briefly conflicted about whether I should call this guy Qingdo a grass thief.

No matter what, the word "foot thief" was more palatable than "foot thief."

Although he was a god who explained the wall-breaking technique in his own way and showed off the operation of the true energy and its movements.

Since I don't have legs, I just lift my upper body and wave my arms around. I wonder how I can climb a wall like this.

In fact, the registration itself was already after a new name was added to the martial arts world just by hearing the news.

Maengbongbubyeok, a wall with a blue border, was named after a fierce bee that was attached to the cliff.

Why were we watching a demonstration of a wall-climbing artist struggling half-assedly without a foot to stand on, even after he has already been provisionally registered?

Well, that's fun.

And wouldn't it be a bit strange to just say, "Oh, I see," and move on after hearing the rumor?

If it's the internal energy method, then it might be okay, but if it's the study of the maternal side, then just the ninefold formula was half the battle. You have to see the demonstration and see the entire beginner's mind to be able to understand it completely.

"Something's a bit off. I thought I was supposed to be able to cling to walls and fly around like that. Like, like, a lizard or something."

When you say a creature that crawls on walls, nothing comes to mind other than a lizard.

But I think it would be really fun if you get used to it.

Walking around stuck to the wall, wow, how on earth do you put up with this?

But the reality of the wall was very disappointing.

The outbreak was amazing.

"No, what were you talking about? How can someone stick to a wall?"

"Wasn't it possible to just use your internal energy? Those masters of Hyeon-gyeong could fly around on swords and stuff. If you can fly, why can't you stick to walls? Old man? You could fly around on swords too?"

"If it weren't for those political bastards, Nobu would have done the same."

Since Killler Demon has put aside her pride, she quickly answers Qing's question.

Of course, blaming the political party means that it was not possible.

Well, the sword flight requires specifications that were at least equivalent to those of a mid-sized aircraft.

Even though he was a master of Hyeon-gyeong, it seems like he was completely destroyed in the beginning.

It was said that Qing, who thought the sight of him flying while riding a sword was cool, asked Ximen Surin directly.

You can do it in the early stages of the current state, but you can only really fly if you concentrate all your mind on it, so let alone moving, you'll just be floating in the air and gaining internal energy or something.

"Well, at Hyeon-gyeong's age, you could probably crawl around on walls with a suction cup. But why would Hyeon-gyeong's unmanned personnel sneak around on walls? They're superhumans who can fly three at a time with a single jump."

"Hey. Since you can't do Hyeon-gyeong, you have to learn the wall-climbing technique separately, right? So I was wondering if there was a secret to climbing walls like a lizard. Isn't it just about putting strength into your fingers?"

"That's what's important, isn't it? Do you know how firmly a human's fingernails cling? If you stuck your finger in a wall and climbed up and down, it would all fall off in less than a second. The key was to protect your fingertips—"

"Hey. It's nothing."

It was Qing who had fingers that could easily block even the indestructible Geumgang Sword that was already given to him by Minor Magicians.

Isn't it just a finger technique that can effectively climb a wall, a technique to use against a wall?

Well, it was my fault for expecting something just because of the blue border.

By the way, if you want to have Jeong Byeokho-gong, you can just ask the master, that is, Cheon Yu-hak, and he will teach you the best new skill among the Byeokho-gongs.

Of course, Shinto and Byeokho-gong were inseparable.

Cheon Yu-hak had simply been busy and forgotten, and knowing Qing's immense strength, stamina, and lightness, he was not in a hurry.

Wouldn't he be a disciple who could climb the cliffs on the ceiling with just his strength, even without a wall guard?

anyway.

Qing speaks as if she was doing a favor.

"Well. Anyway, I worked hard. I'll prepare dinner for you later, so it's not like it's a loss, right? My legs were crippled, so I've been lying down all day, so it's nice to finally be able to move."

The tendons on both sides of his forehead flared up.

But I endured it.

"And, Jeomsoi? Something's getting weaker? Yeah, strong. Oh, oh, that feels good."

Qing sits in the hallway, looking into the brain of the god of illness, and leans against the iron bars on the other side.

And two fists coming out of the iron bars were patting Qing's shoulder.

Maduro, who has a wart the size of a fingernail next to his nose, was debating between "Spray" and "Wart", but chose the nickname "Spray" because he thought it would be more insulting.

"Hehe, does it feel refreshing? I told you back in the day, I was called the Stone Fist. One-hit, one-fisted fist. Anyone who got in my way was knocked out in one hit."

"Wow, it's worthy of being called a stone fist. The punch was truly exceptional. But was the strength of the devil worth using? Just a little on the back of my neck, oh, there. Wow, this was crazy."

As he rubbed the hollow area behind my ear, I couldn't help but let out a pleasant moan.

But, wouldn't it just change back to a pat pat after just a moment?

"What the heck, I thought it was starting to feel a little better. Why did you stop kneading it?"

"Ugh, since the vein was cut, the strength of the demon was not going in at all. Please take a look at the situation."

The original hollow acupressure point on the upper back of the neck was so cool that the masseuse squeezes it with great effort.

Moreover, it was a point where the vein has been cut off.

He has a basic weight class, so he wouldn't really lose to a ten-year-old kid, but he's in a position to be a match for them based on pure brute force.

Qing-i pats her shoulder, enjoying the cool shock as she loses herself in thought.

It's now the fourth day of the Repentance Hall.

I've completely scraped up all the martial arts, so much so that just looking at the list of martial arts temporarily registered in the martial arts store was enough to fill me up.

Well, I'm full, well, I'm hungry.

Anyway.

Tomorrow was the fifth day, the day when all five days ordered by the Great Master Jangmun will be fulfilled.

Well then, now it just needs to disappear.

What's the best way to disappear so that Cha Xiantian, the Annihilator of Doors and King of Apparatus Formation, can became a deep memory that these bastards would never forget, kicking the blankets off every night?