\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (15)}

The truth was an illusion that exists.

It was a method of influencing people by twisting the energy of nature, so that people's senses were distorted, they see illusions, and they cannot come to their senses.

Those who have not experienced the truth click their tongues and say, "Are you struggling with that illusion and empty things?"

If you look from the outside, it would be chaos, with people circling around in the same spot, or fighting alone on the bare ground, waving their swords in the air, kicking the ground, and rolling around.

But it wasn't a simple illusion that could be escaped just by knowing it was a lie.

What if I knew I was trapped by the law?

It was claimed that all the senses of the eyes, nose, ears, tongue and skin were not false but real.

So, for me, it was a very real phenomenon, and my skin was split open and cut, I was hit and my bones were broken, I sweated profusely even though I wasn't hot and died from shivering even though I wasn't cold.

Of course, it was extremely rare for a person to be tricked to death by the effects of the method alone.

Most of them just keep you locked in circles until you break free, or they show you something mentally harmful that causes you great harm.

And to deal with these wandering people, the Living Gate exists.

In the formation, a living gate refers to a place that was not affected by the formation and a path leading outward.

So, by laying down a strategy and dealing with them using poison or traps, or by having those who memorize the text go in and deal with them directly.

Manra Daehyeolmyeolcheonjin was a blood cult's annihilation den notorious for its fear and bondage.

The world was in such a terrible state that the faint-hearted will immediately faint and lose their senses.

Even if you have the stomach and liver to endure it, you will still become powerless.

You were held captive by countless fleshy arms extending from the fleshy earth, unable to move, and you were forced to lie down, subdued.

Manra Daehyeolmyeolcheonjin was notorious for having no living beings at all.

Anyway, all kinds of monsters used by the Blood Sect were created that way because their formations don't work.

Moreover, even if they were somehow rescued, there were countless cases where they become disabled due to the terrible memories or suffer from nightmares for a long time.

anyway.

It doesn't work on the blue.

Just like it was at Cheonmachong the other day.

So, I strode forward with brisk steps and searched every inch of the huge temple of Hyeolryoeumsa.

But where on earth was the center?

At first I thought it would be easy to find.

I just thought that if I went into the largest building, a structure made of bones and internal organs, I would just come out.

Well, if you think about it a little, that's not possible.

A master who has reached the level of Hyeon-gyeong can see through the formation, but in reality, it was not easy to confine even a Hwa-gyeong for a long time.

In a formation, there was a core that holds the center and a skeleton that supports it, such as an object, a person, or a building.

So, if a person of the level of Hwagyeong were to spread his energy in all directions and destroy everything he came across, the formation would eventually collapse.

So, wouldn't the more advanced the formation, the more likely it was to be buried in the ground so as not to be destroyed, or hidden so as not to be shattered by a blind sword?

So it's only natural that Qing was lost.

Qing was searching through the fourth Buddhist scripture of Hyeolryeumsa Temple.

"hey?"

Suddenly, Qing turns around, aiming her sword at the sound of someone calling her.

A head sticking out over the wall.

However, the wall was shaped like a writhing, white skeleton and parasites protruding from the inside of the body.

Thanks to that, the head of the woman who was smiling brightly in the meantime ended up being a rather strange scene.

"It's the Thousand Flower Sword, right?"

Qing slowly lowered his sword.

It's very, very suspicious though.

First of all, I use polite language.

The eyes that sparkled without hostility resembled the longing of the young girls who would occasionally stop by the small and medium-sized sects and greet Qing with a squeal.

"who were you?"

"Wow, it's really the Cheonhwageom! The most beautiful woman in the world! Is it really as they say? I heard she's a beauty queen. Could you show me just this once?"

It was a terrifying reaction, as if I had entered the body of a giant monster and was surrounded by grotesque internal organs.

After wondering what to do, Qing obediently pulls down her face covering and reveals her face.

Then the woman's eyes open wide.

And then he nods his head as if he was satisfied.

"This filthy woman! A thief cat! You seduced me with that face! I approve, I approve vehemently!"

"hey?"

"Ah. Right. Manrahyeolcheondaehyeoljin? Manrahyeolgyeopdaemyeoljin? What was it?"

Qing shrugged at him.

Because I don't know exactly what's going on!

Blood cult kids just want to show off and give themselves difficult names for no reason.

"Anyway, you came here to find the center, right? Okay, let me show you. This way, this way."

Qing-i, um.

Is that a ghost or a person?

Although the method doesn't work, isn't it a unique ability to see into other people's illusions?

Qing follows the woman and looks at the numbers of the Western Regions above her head.

First of all, the number of evil deeds exceeds 100.

He's a villain, but he's not on the level of the Blood Cult guys I've seen so far.

What was it? What kind of woman was she?

Isn't it a trap?

Well, even if that's the case, there's no guarantee that we'll find the center of truth just by continuing to fall behind like this.

I thought it might be better to just stick my head in, even if it's a trap.

The place I followed the woman to was the third building I had visited, which I had just turned upside down.

"I looked for this place earlier-"

"Hey, you didn't find it right. Here, here, here."

The woman was groping the floor, her rumbling intestines, and then suddenly, with a bang, she lifted out a part of it as if she had cut it out.

Below, where the thick blood stretches like grass, a passage leading underground was visible.

"Okay. That's all for me. My name was Siang, meaning "woman born under the sun." You have to remember it, right? Oh, and by the way, I'll keep it a secret! The Blood Cultists might try to kill me."

"for a moment-"

"Can you pretend not to know me next time we meet?"

The woman, Siang, shouts and immediately flies towards the wall.

A squeak, the sound of a wooden window breaking. Ah, that must have been a window.

Siang, who had passed by in a flash, quickly disappeared at a great speed.

Qing tilted her head.

What was it?

It's extremely flimsy for a trap.

Or it could be a trick to lure them into a trap by pretending to cooperate obediently and making them feel at ease.

However, Siang's attitude was so friendly that it was like meeting the idol I admired.

If that's acting, then it's so great in its own way that I think I should be fooled.

So, Qing goes underground with his sword in front.

Due to the influence of the formation, the whole place was still covered in internal organs, internal fat, bones, and parasites, so it was a very unpleasant sight.

The path down to the basement was deeper than I thought.

I thought I had come down to about the third floor, but suddenly, at the end of the stairs, a thick iron door blocked the gap between the flesh.

The iron gate was covered in a series of talismanic charms that were obviously of a strange kind.

He was relieved.

It seems like the woman guided him properly.

Did you say Siang? I should remember that.

Qing pushes the door hard.

It was a power that transcends humanity, yet it was so tightly locked that it does not even move.

If it doesn't open, just cut it.

A sunset glow rises from the Moonlight Sword.

Starlight seeping through the iron gate.

When I touched it with my hand, I felt that it was a solid piece of iron, about two inches thick.

The Moonlight Sword's energy changes its form, and jagged thorns begin to grow along the blade.

Three soul lights clearly appear in Qing's eyes.

This was the front wheel of the ten greatest magicians in the world, the front wheel of the magic kalpa.

And the moment the soul flame slowly begins to rotate-

"ah."

Qing found the handle attached to the corner of the iron door, put away his sword, and pulled it.

Then, a loud squeaking sound of scraping iron rang out.

Ah. It wasn't Missio, it was Danggisio.

And so the interior of the basement was revealed!

As soon as it opens, a pungent smell of blood emanates, and it explodes out.

"Ugh."

His expression was like, sniff sniff. Ugh, the smell of blood.

It's so fresh? It's really good.

People were subjective beings.

Blood scent was not a bad smell to everyone.

Qingi huffs and puffs, filling his lungs with the smell of blood as he enters the hidden basement.

Then, what unfolded before my eyes was the interior of a perfectly intact stone chamber with walls made of stone, above and below.

But with real human organs.

It was a fairly avant-garde style.

Hearts, lungs, and livers were strewn everywhere, and internal organs hung from the ceiling, nailed down.

And in the middle of it, countless letters were written in blood, no, they weren't written.

They dug a hole in the floor and poured blood into it, so it was amazing how they were able to carve out and etch all the detailed text.

And in the middle of it, there was a pile of meat, with the top of the head sticking out.

What were you doing, kid, rolling your eyes?

A child with a still youthful face was buried inside a piece of meat.

Qing was so startled that he jumped forward in one step, digging at the flesh in all directions, and the moment he reached out to pull the child out-

The blue one suddenly stops moving.

The pupils rolled up, revealing only the white sclera, and the mouth was wide open, oblivious to the drool that had accumulated due to the scent of blood, dripping down and forming a ball on the chin.

The feeling that the world itself does not exist and that one was floating alone.

There was nothing, not even nothingness, so there was only chaos, a mixture of light and dark, an emptiness that cannot be seen or felt.

In it, Qing feels the blood thunder sound.

That was a very accurate expression.

The Blood Thunder Demon was inside me.

Because that vast temple was like a part of my blood, flesh, bones, and organs.

To be exact, it was not a blood thunder sound.

The formation was the inside of Qing and Qing itself, and the Blood Thunder Sound Master only felt that way because he was within the realm of the formation.

Qing understood the situation in an instant.

Ah. This. That's it.

I become the truth.

Then, Qing completely understood everything about Manra Daehyeolmyeolcheonjin.

That's because the blue was the true method and the true method was the blue.

And isn't the unmanned Hwagyeong the one who fully understands himself?

Inside the Cheonmachong Tomb, Qing saw the most painful memories that the Demonic Cult warriors had hidden deep within their hearts transformed into images of the world.

This was a terrible method that tore at each person's memories and personal wounds.

However, Manra Daehyeolmyeolcheonjin was a world made up of only one person's imagination.

The center of the truth that communicated with the ominous star of the Thousand-Year-Old Castle, the child that Qing was trying to save.

Qing sees the child's memories for a moment.

I have made countless people die by torturing them with a knife, and I am a child who only eats the blood and flesh of the humans I slaughtered.

Also, to the child, humans were nothing more than things to kill or things he wanted to kill.

Also, the blood cult members abused the child.

The indifferent expressions of the blood cultists who beat, whipped, and flogged him were not for fun, but because it was abuse born of necessity.

In this way, the child was instilled with hatred and also learned hatred.

That's how the murderer, the murderer, was created.

Before Qing could even begin to rage at the horrible creation, something dawned on him.

A murderous spirit artificially created by a malevolent force unfolds its image in the center of the truth.

It was the core of Manra Daehyeolmyeocheonjin.

And now.

The blue reached the center of Jin.

Qing became the law.

Not a fake one that was forcibly attached to a bad star, but the true owner of Heavenly Slaughter.