\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (4)}

"Why, why do you go to such lengths? I've already told you everything I needed to know. What had this old man already locked in his cell do that offend you? Why…"

Killer Demon's voice trembled.

But Qing's responds with a snort of excitement.

"Huh. Did the old man have to have some grand reason to kill someone? You just didn't like them. Wasn't that all? It's just that it's the old man's turn now."

Then, Killer Demon's lips moved as if he was about to say something, but he couldn't bring herself to say it out loud.

Lips trembling, eyes trembling slightly to match, and fingernails covered in dirt.

His shoulders slumped, and his back hunched over, making him look like he was hanging on to an iron bar.

He was a former great Demonic Adept who would sit upright and pretend to meditate, but now he has undergone a dramatic transformation into an old man who has aged rapidly, as if he was trying to live up to his age.

The beads of sweat on his forehead grew larger and larger, eventually flowing down his cheeks and past his eyes.

Qing looks at the sight as if possessed.

Killer Demon's eyes, the pupils dilated to the point that they seemed to be nothing but black holes, the eyes were the windows to the soul, and the dull pupils reveal an empty emptiness.

Qing bit her lip slightly.

It's a pleasure she never felt before.

Inversely proportional to the blurring of Madu's gaze, Qing's pupils sparkle, and Qing's heart beats as fast as the rapid passage of time that makes people age.

It was a decline of the mind and soul that was visible to the eyes.

The moment when someone completely falls apart.

Qing gritted her teeth to control her trembling body.

And yet, she stared at the old murderer's figure with heavy breathing, as if trying to engrave this image in her mind forever, so that she could recall it endlessly.

Perhaps that insignificant old murderer of a generation will never meditate again.

You won't be able to straighten your back and hold the weight.

But that doesn't mean that the dirty desire to secretly pick up food that fell on the ground and eat it hasn't disappeared.

Rather than being an old man who waits helplessly for the day to die, I would rather he live a long life, holding on to what little life I have left and suffering.

Qing gets up from her seat.

The prisoners' heads follow him.

"Okay. It's time to go. I was planning on taking one of you with me. Let's see."

As Qing looked around the inside of the Repentance Hall, she suddenly burst out laughing.

The refreshing sound of laughter echoes throughout the hall.

If the voice didn't come from a bloody thug, it would have been a really clean and clear sound, a sweet voice that would have permeated their ears.

"No, everyone, ugh, they're really bright and cheerful."

Aren't all the prisoners sending out earnest looks of anticipation, unable to let go of their expectations even in the midst of all this?

How can you not burst out laughing when you see this?

Aren't they the devils who committed heinous crimes and shed the blood and tears of hundreds of innocent people?

It's not like the guilt will go away just because he acted cute for a few days, so what's with this confident appeal that he must be taken away?

"Now, there's only one person who can get out of here. It's my choice."

Dududu, imitating the sound of a drum being beaten.

Then, the bastards of Repentance Hall swallowed their saliva and couldn't hide their tension.

And then Qing finally announces the lucky winner.

"That's you, the Heavenly King of Apparatus Formation, the Annihilator of Doors! Congratulations, Young Lady Cha Xiantian!"

Qing speaks and answers alone.

"Oh my, what an honor this was to me. Wow, how can I possibly express my gratitude? First, I'd like to thank all you damn bastards gathered at Repentance Hall. Thanks to you, I realized I shouldn't live like this. This is what happens when incompetent bastards were greedy and have bad tempers. It is a valuable lesson."

The prisoners' expressions were half bewildered and half dumbfounded, as if they couldn't understand what was being said.

Either way.

Qing's eyes shone brightly and sparkle.

"Well then, Young Lady Cha Xiantian, in addition to your escape, you will be provided with 11 servings of food for your snacks. Oh, maybe you are willing to use it for a good cause?"

He grabbed the handle of the food cart.

"No. I'll eat it all myself. I'll monopolize the prison food. Your breakfast has been repurposed to my escape rations. I'll always be grateful."

"Wait a moment-"

"Goodbye, everyone! I'm leaving this shackles and bonds of this repentance hall and going in search of happiness! You can stay being miserables!"

Then, she bowed her waist, bent her right arm, and pulled it towards her chest. Isn't this a polite bow in the Western style?

Of course, no one would be wise enough to know that this was a Western greeting, but they will probably remember it for the rest of their lives.

Then, she opened the door to the outside and pushed the food cart to carry it out whole.

"Wait a minute, that's not what we agreed, hey!"

"You bitch! Why are you taking my food! Leave the food behind, you fucking bitch!"

"Hey, you little bastards! Prison break, it's a prison break! That bitch is escaping!"

The belated old voices burst out all at once and gathered together in one lump.

The screams, which were made with the blood in their veins and the strain on their vocal cords, became an incomprehensible roar that rang out so loud that it was deafening -

Thump. As the door closed, the commotion beyond the wall faded into the eerie background noise of a market outside the inn.

Rather, wouldn't it be noisier outside after passing through the middle gate and opening the outer gate of Repentance Hall?

There was a lot of uproar, with people screaming and yelling that even a palm-sized window had pierced every brain cell.

-Prison break, prison break!

-That girl was getting out of there! Bastard! Bastard!

And there was one Kunlun Taoist named Bastard, who listened to the yelling with a calm expression.

"Are you done?"

"Yes. Wow, I've had a lot of fun since the start of the New Year. But I got carried away and brought their breakfast. What should I do?"

"Didn't you say you were going to throw it away?"

The original plan was to have breakfast for you guys, but then there wasn't.

But that just wasn't possible.

"How can you do that to food that hasn't even been touched? And someone else has to clean it up, so it's a nuisance."

No matter what, you can't throw away perfectly good food, right?

Especially since he was so hungry, how could he just throw away raw food when he would rather feed it to a stray dog in the neighborhood?

"That's great. I can give it to them for lunch."

Qing looked at today's breakfast.

\textit{Carrot porridge with a good amount of meat.}

\textit{And fried meat, what about this meat?}

Qing put a piece of meat in her mouth, munching on it. \textit{Oh, this is beef.}

\textit{It's fried beef. But it's not marinated.}

For reference, today was the 5th of the month.

Besides, it was the middle of winter in the cold land of Qinghae.

Breakfast left outside would not only cool down, but would also become a cold, refrigerated food.

In other words, the prisoners' lunch today was scheduled to consist of carrot porridge floating on shaved ice and fried beef that was so cold it was almost cold.

\textit{Huh. Where can I get something luxurious to eat like this?}

\textit{If only someone had given me this much when I was a beggar.}

\textit{I was so overwhelmed with joy that I couldn't tell if it was my birthday or the last supper, if it was a dream or reality.}

\textit{First of all, they must have eaten it greedily so that it wouldn't be taken away, and it was so delicious that they shed tears of gratitude.}

\textit{But if they're complaining about side dishes, is it worth giving to them?}

\textit{These bastards are really spoiled.}

Qing was thinking of mixing a handful of dirt into the carrot porridge, but then she thought, 'You can't mess around with food, can you?'

"Well, but wouldn't Danlun Zhenren be the one cleaning up the floor then? I think I got too carried away and went wild… Should I cover my face and clean up the blood that was splattered?"

Danlun Zhenren shook his head at her.

"It's my turn now. You must have been uncomfortable, so get some rest. We can talk about Taoism later."

For some reason, the Danlun Zhenren who said that looked very excited.

\textit{I'm really sorry for the mess, but it looks like he doesn't mind, so I guess it's okay.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Repentance Hall was always noisy.

But that was it.

Even though they were making a lot of noise about jailbreak and the summer bitch, there was no response and things just gradually died down.

The rumor inside was that the Kunlun faction was devastated when the two of them escaped last summer.

Judging by the way she even uses that thought, she must have been a bitch who had gone beyond being possessed.

If you've gathered only four of the ten greatest demonic forces in the world and were running wild and causing chaos, how can you possibly afford to worry about things like the Repentance Hall?

But so what?

Even if the prison was abandoned, what can the prisoners do?

I wouldn't just clutch my hungry stomach and leave it like this, would I?

I'm not going to starve to death like this.

If there was a problem in Kunlun right now, would you take care of places like Repentance Hall?

So, even the prisoners who had been talking loudly soon lost their strength and collapsed.

Time passed like that, and finally the inner gate of Repentance Hall opened and the sound of a food cart being pushed in could be heard.

"For lunch today, we have horajuk and hwawooyuk."

"Hey, is this the time to have a peaceful lunch? What happened to that Cha Xiantian girl?"

Danlun Zhenren blinked his eyes, and blinked again.

And then he asked as if he didn't understand what they said.

"Summer tea\footnote{literal meaning of Cha Xiantian}? What are you talking about?"

"That bitch, the White Hand Witch! No, I mean, that Black Palm Purple Lightning Chakra Witch!"

Danlun Zhenren scratched his chin.

"Did you have a dream?"

"No, the girl who was locked up there!"

"You're out of your mind. That room has been empty the whole time. The door was broken, so the cell was never used."

"No, that's why she were so docile even though it was open, so you thought she was special and even gave her a lot of food to eat!"

"Who's going to eat in there? Me? Why would I bring my own food all the way to Repentance Hall to eat it?"

"No, you, that is-"

The dumpling ears make a weak sound, "Ss …"

"Damn it, you're trying to pull some bullshit like it never happened just because you missed that bitch now! Ha, you bastard, then what's that pool of blood over there? Pig's blood? It's clearly your Kunlun's bastard blood, isn't it?"

Yes, it's pig blood.

Danlun Zhenren looked down at his feet.

Then he lifted both feet and put them down.

Amidst the loud sound of blood splashing.

"Blood? What kind of blood are you talking about? It's clean."

"No, it's splashing just right now-"

"This is why you guys are hallucinating. I served you a sumptuous meal this morning, and you're so full of energy you're even making a fuss."

"No, when in the morning-"

"I definitely gave five-spice pork, tangchoyuk, sujoyangtang, and a whole Peking duck per person. You were so quick to eat that you didn't even say a word, but now you seem still full."

Danlun Zhenren told lies very calmly.

The prisoners just opened and closed their mouths.

"You little shit, stop messing around-"

"You're probably dreaming around like this because the breakfast hasn't been digested yet. So I'll serve lunch in the evening."

Drdrdrdr, it was the sound of the Danlun Zhenren pulling the food cart and leaving again.

"Hey, wait a minute-"

An urgent voice catches Danlun Zhenren.

It was the desperation of prisoners who had skipped breakfast and now had to skip lunch.

But even so, how can prisoners locked in iron bars catch a determined person?

Danlun Zhenren, who was closing the door, snorted deeply and then forced himself to suppress the sound of sobbing.

It was the way that the Danlun Zhenren enjoyed himself.
