\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (11)}

There was an ominous rumor going around downtown Xinying.

There was a rumor that the Blood Thunder Demon had gone mad and was wiping out the entire Jangjok village.

I heard that there were no houses left around Chachapchon, and that in Cheonjunhyeon, a strange monk executed the lamas who had committed a crime.

A terrible rumor has been heard since the new year, and everyone was murmuring in the winter when there was nothing to do.

Some people call it a conspiracy.

Some people even said that the head of the Blood Thunder Temple had gone crazy, so whenever people gathered, they would bicker and argue, and it was like there was no other temple that was the talk of the town.

Then, the day after the Lunar New Year.

A one-armed lama appeared in the city of Xinying.

Because the lama was such a famous figure in Qinghai, word of his identity soon spread throughout the city.

The Strange Monk Amukhaprap!

He was a skinny old man who was also called a doll bone or a bone shaped like a human.

But what about now, when the left arm of the lyricist was fluttering empty?

The cheeks were completely sunken and dark, like gaping holes.

The eye sockets were also of that shape, but the eyes were so sharp and filled with anger that it didn't give that impression.

The monster slowly crosses Xinying.

The monster's expression was filled with murderous intent, so the people of Xinying, though fearful, did not hesitate to follow him.

Because this was the spirit of Zhongyuan people.

Master of the Jo Gyeon-tu!

If I can see a fight in the morning, I'd rather die in the evening and live my life to the fullest!

For reference, this was a twist on Confucius's words that one should risk one's life in the pursuit of enlightenment.

Anyway, as people flocked to follow the monster, the crowd grew larger and larger, filling up the main street of Xinying.

Where was the monster going?

Looking at your expression, it looks like you're going to get angry. Isn't this something out of the ordinary?

Then, the monster reached the central square of Xinying, and moved quickly towards the merchant who had taken a good seat in the center.

The poor merchant rolled his eyes.

"Oh, monk? Why were you asking me…?"

"I borrowed your thoughts."

"Ah! Yes! Of course!"

The merchant, with an expression that showed he had endured ten years, cleared his throat and took a good seat in the front, looking at the crowd of onlookers who had gathered.

It was a dramatic transition from merchant to spectator.

Since it's not my job, I suddenly become curious.

"The name of the great self-"

"Oh." "Monster!" "Yah!"

The monster only uttered a few letters, but many people immediately called out his names.

After all, there was only one lama in the world who calls himself the Great One.

And the person from the middle class wanted to show off his culture by pretending to know it, so the impatient cultured person shouted before others.

"Great Self, to you, um, there exists someone, someone who speaks the Great Language and was fluent in the primitive Chinese language. This was an opportunity to acquire immense merit by assisting Great Self."

People were collectively bewildered by him.

But there were some who understood.

This supports a high level of language comprehension, so it could be said to be a very effective way to select a clever interpreter.

"[The head priest of Blood Thunder Temple has gone mad.]"

"The head monk of Hyeolryeumsa has gone mad-"

Pfft. The head of the tall man in charge of the interpretation sways with a loud noise.

"[This one, convey my words clearly.]"

"[Yes, yes!] The head priest of the Blood Thunder Temple has gone mad!"

The crowd was bustling and noisy.

Then the monster stretched out his hand and said, Oum-!

The sound of the Great Master's clearing mantra instantly silences the crowd's commotion.

"[Lunduprinjing, that author has gone completely mad. He has long advocated for the purity of the Zhuang people, but now he has completely lost his mind. He regards all Zhuang people who wear, eat, and use the customs, food, clothing, speech, and writing of Zhongyuan as traitors of an impure race, and he intends to exterminate them from the world.]"

"Huh."

The daily interpreter was the first to gasp in surprise, and then the Jang tribe of Xinying followed suit.

Only those who don't know the director's words can wonder what on earth he was saying that makes them turn pale as soon as they hear it.

But that was only for a moment, as the daily interpreter began to grumble again as he translated the language into the native Chinese language.

'No, what the hell was this nonsense?'

'You have to be crazy to say something like that-'

'That's why I said you're crazy.'

'Oh, I said you were crazy. Now that makes sense.'

'Shh, I'm talking.'

"[The madman's delusions didn't stop there, either. He also insisted that all but the purest of the Jang tribes in Qinghai lands be exterminated. Yes, I'm referring to you, you poor people of Zhongyuan.]"

This time, the faces of everyone except Jangjok turned pale.

Now, isn't it no longer your job but your own?

"[They have already annihilated nine villages, wreaking havoc. They have completely wiped out everyone, regardless of age or gender. The monk tried to stop them, but it proved too late. Instead, he surrendered his arm and fled miserably.]"

Then the monster lowers his upper body and lifts the class leader with his remaining hand.

"[This incident occurred due to the insufficient power of the original monk, and the inability to grasp the madness of the author Runlin. The original monk sincerely apologizes.]"

The room was filled with silence.

What kind of person was the monster?

It was rare in the martial arts world for a master like this to personally apologize, let alone a monster.

It also contains a lot of sincerity.

Among them, the people of Jangjong shouted, kneeling on the ground in this crowded, narrow space-

"Raise your head!"

"You have nothing to apologize for!"

"Please refrain from such excessive words!"

When he hears that, the back of the clown behind the Amukharap suddenly pops out and stands out.

It was the result of a person clenching his teeth.

"[We must stop the maddened Blood Thunder Demon. However, since this monk's power was beyond our reach, I am only asking for help with a presumptuous heart. That is, from the Taoist monks of the Kunlun sect, those who uphold the Way.]"

People realized the monster's intentions.

This was an accusation of the Blood Thunder Demon's murder, and also a public beg to the Kunlun Sect!

More discerning people thought.

By gathering such a large number of people, the monster also revealed his own shortcomings.

Even the justification for destroying evil there was correct, so isn't it true that Kunlun was in quite a difficult situation?

If you refuse, you will lose a lot of face as the representative of the Jeongpa martial arts world that aims for righteousness and as a great Taoist school called Gupa.

If you accept, you will bleed.

Of course, I didn't think it was all planned out.

"[Therefore, I, the Venerable One, wish to go to Kunlun and ask for help directly. Those who were willing to join me and raise their voices, so that we can accumulate merit together, and this was what I, the Venerable One, ask of you.]"

So Amukhaprap takes a step forward.

And people follow suit.

Some people plan to help the monster and ask Kunlun to fight together, while others were simply curious about Kunlun's reaction.

However, the number was so great that the road leading from the west gate of Xinying to Ilwolsan was filled with people, and they seemed to be flocking together in one mass.

Half a day like that.

In front of the crowd that followed, even skipping lunch, the neatly dressed Kunlun sect Taoist priests in front of the mountain gate came into view.

And among them, an old man with wrinkles all over his face and a fresh air was looking at the audience with an upright posture despite his appearance.

The old man steps forward and offers a polite nod.

"I am an old Taoist monk named Tian Feizi. May I ask why you have come to the mountain temple in Kunlun?"

"Tian Feizi!" "Kunlun Jangmunin!" "Baekunseon!"

Commentaries that were followed without fail.

Then the monster takes a step forward, shouts a curse, lifts the class leader, and bows.

"[My name was Amukhaprap. I implore you, Sect Leader, for the sake of all the people of my land of Qinghai. Please lend me your strength.]"

Thus, the lines that have already been agreed upon were spread to everyone through the commoner interpreter.

(Chewing blood) Those bloodthirsty bastards were bad bastards.

(Surprised, as if hearing it for the first time) What? How can a person do that!

(Half embarrassed, half desperate) I know it's shameless, but please give those kids a lesson.

(Pretending to be troubled) Ahem. But we also have our own circumstances. Ahem.

(Kneeling) Please, to prevent the destruction of the world's peace, to protect the peace of the land of Qinghai.

(Pretending to be even more embarrassed) Oh my, Monk, please get up?

(Especially loudly and powerfully) Please punish those horrific villains and prove that justice still exists in this world and that the evils shall be destroyed. Yes?

(Looking very, very embarrassed) We'd like to do that too, but, ahem.

(Be careful not to make it look like you're throwing a tantrum, with a grave voice and sharp eyes.) I won't move until you help me. Either rip my stomach open or step on my corpse. I'll live here, so Kunlun can do whatever you want, whether you come up and help me.

And then, Amukhaprap got down on his knees, closed his eyes, and started chanting.

Of course, the Kunlun sect needed to have an attitude of thoroughly considering the requests of the monster monk.

Even if the opponents were people who deserved to die and there's a clear justification, isn't it the case that a huge sect like the Kunlun Sect was attacking a small sect?

Without this process, it was inevitable that there will be talk that the Blood Thunder Shrine subjugation was an excuse to seize control of Qinghai.

On Nine Sects level, its influence was enormous.

'The Kunlun Sect did the same, so why can't I?' That excuse would definitely cause a bloody storm throughout Jianghu.

So the Strange Monk stood guard in front of the mountain gate of Kunlun for three days and nights.

Without eating or sleeping, he kept chanting.

The number of onlookers watching the scene gradually increased, so it was questionable whether the Kunlun Sect would respond to the request or not.

Some even kneeled and chanted the same prayers behind the Strange Monk, and finally on the evening of the third day.

This was what the Tian Feizi, who came down with the Kunlun warriors, declared while looking at the Strange Monk.

"I have lost. Moreover, if what you say was true, if we neglect those evildoers, a great bloodshed will continue. We cannot turn away from those in need for fear of shedding blood. Therefore, Kunlun will help you. If we don't go to hell, who will?"

And then he personally raised the Strange Monk and supported it, and it was the moment when the Kunlun Sect declared the subjugation of the Blood Thunder Shrine.

At that moment, the quiet Ilwol Mountain shook with a thunderous roar.

Everyone's hearts have become swell.

As if they had witnessed some historical moment.

And amidst the cheers, there was one person who observes the crowd with a blank expression.

\textit{Why are they cheering?}

\textit{Because the scene just now was touching?}

\textit{Intoxicated by the anecdote of the monk who knelt for three days and begged for revenge and salvation of all living beings, and the Kunlun sect who responded?}

\textit{Because I ended up agreeing with that definition.}

\textit{In other words, isn't the Blood Thunder Demon the world's greatest evil to them?}

\textit{Anyway, humans were like that.}

The woman shook her head slowly and then began muttering to herself.

"Sister, are you doing well? What's wrong? You stuffed her under the bed and fed her dog food? That's really too much. How could she be hungry? Oh, yeah. The current situation is, yeah. yeah. I don't think the ultimatum will go through. It seems like they'll just make up an excuse to go to the subjugation and invade right away. Yeah. Who? That Cheonhwageom guy? Is he still in Kunlun? I haven't seen his bare face either, yeah. I've seen it. She's beautiful just by looking at her eyes. Yeah. Yeah. See you later then."