\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (9)}

Wunue was serious.

He was seriously talking about applying quota system to the Nine Sects disciples to become Ximen Qing's close friends.

Even the listener was serious.

Well, Tian Feizi was also the head of one of the Nine Sects.

But now there was something more important than that.

"It's not right for a Shaolin disciple to approach a woman, so for now, let;s the Eight Sec-"

"Uh, Senior. I apologize for interrupting, but first, let's hear about the situation with those Xizangs…"

Only then does Wunue cough with a look of regret on his face.

Come to think of it, he didn't come to see Heavenly Blossom Sword, but rather to respond to Kunlun's urgent request for assistance.

"That's it. First of all, near Henan, not the Henan Provinces, but a town about 550 li south of here. There were bandits there…"

Tian Feizi revealed the suspicious bandits of Henan and their true purpose, the atrocities of the Blood Thunder Shrine, and the rescued Strange Monk.

"Huh, those so-called Buddhists. Well, actually, lamas are more like government officials. They're just idiots, aren't they? Even so, how can they pretend to worship the Buddha?"

Wunue muttered as if he really pitied them.

Apart from that, Tian Feizi's explanation was very easy to understand as it was organized in chronological order.

This was entirely because Tian Feizi was telling the same story for the second time.

When I was explaining to Ximen Surin, I stuttered and left out a few things, because it was my first time relaying the incident.

And it was probably because the godmother was a senior who was much more difficult to deal with than Wunue.

The first explanation was blundering, the second one was much better.

And four days later, on the second day of the Lunar New Year.

The third explanation of the thousand-year-old's work was supplemented with fluff here and there.

Wouldn't it have been a great story, complete with the activities of Cheonhwageom and a major twist in Xijang's plot?

A middle-aged man who heard the story expressed his admiration.

"Oh, you're saying that Cheonhwageom kid was that great? As my senior who has been inspected, I'm so pleased. I was thinking I should treat him well for his sake anyway."

"Hey, I'm not talking about the Cheonhwageom, but I'm saying that the problem was those guys that were under the command of the chief."

Tian Feizi's speech was not the only thing wrong with him, but his posture was also very awkward, as he sits with his arms crossed. This was because he was a long-time friend of a middle-aged man.

Of course, the so-called face value, that is, the person who appears to be a ninety-year-old man, was a commoner.

It might seem odd to be friends with a middle-aged man with only a few wrinkles on his face, but if that's unfair, you should have gone to the police station and turned back the clock.

Just like a middle-aged person.

A middle-aged man chuckles and waves his hand.

"You worry too much. With senior Wu-Bul, senior Mad Dog, and even this Dae-Mo, what's there to worry about? With three Profound Realm masters, we could even raid the palace."

"That mouth is inviting a disaster."

"No, did I say something wrong? You wouldn't report it anyway. My nickname itself is already treasonous, so what's the big deal about a little joke?"

The man with the most treasonous nickname among the Ten Greatest Masters Under the Heaven.

It was none other than the King of Swords, Nan-Gong Daero.

Because there was no history of the emperor giving a royal title.

Originally, wouldn't calling someone a king mean a serious crime, a treason, that would destroy not only the entire clan, but also the entire clan of the entire clan?

But the world was just calling it that as they please, and Nan-Gong-daero's official position was that it was nothing more than a mere rumor.

It was like covering one's eyes and pretending not to see, but even in the palace, there was no particular problem.

Rather than being lenient, it was because the martial arts world, which had developed in peace and was in its prime every day, could not be tampered with carelessly.

"Stop tempting fate with that damn mouth. What did you say when your son was still in the womb? You said you'd have no other wishes if he grew up to be a sword-crazed, sword-loving demon. How does that fare?"

"Things are a little better these days, though. At least the two-armed guy isn't acting like he only has one. But that little bastard, ha. Seriously."

Nan-Gong-daero sighed deeply.

Anyway, Nan-Gong-daero was on the same level as Tian Feizi.

You could say that he was in charge of the young blood, being under the same distribution as the top ten masters in the world.

"So, should I just storm in and kill them all?"

"That damn cube. Are you going to kill everyone when Senior Mubul was here?"

"Then why don't we kill them? Shouldn't we stop the war? We need to set an example, and the barbarians will abandon their base ideas. Those Rama bastards seem to be so terribly protective of their own people. Ultimately, it'll only reduce the innocent bloodshed of the Western barbarians. So, if we kill them, won't they go to the afterlife happily?"

"Hmm."

The sage sighs in pain.

"Well, I can't help what the Taoists think, but why were they going on a rampage, threatening to kill all the monsters? So, what's the problem?"

"Isn't it true that resentment breeds resentment?"

"Huh. Those guys think their land was stolen from them. Do you think they'll be quiet, whether they harbor resentment or not? It's actually ridiculous. They were so afraid of the previous dynasty that they offered it for free, and now they're wanting it back."

"Ugh."

"Well, that's fine. I'm just here to be your sword, so just swing me however you want. I hate complicated things."

Nan-Gong Daero said that and then suddenly got up from his seat.

"Hmm? Where were you going?"

Nan-Gong Daero shrugs his shoulders at him.

"I'm going to see the Cheonhwa Sword. Isn't she the future swordsman, and if she does well, she'll become the best in the world? She's also my son's benefactor. How can I just sit still? Honestly, if it wasn't for the Cheonhwa Sword, I wouldn't have come all the way to this countryside town."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Contrary to his appearance, which was quite exemplary for Buddhists, Emperor Geotap simply lay sprawled on a silk pillow all day long.

For the monks of Hyeolryeumsa Temple who had been expecting the famous sermons or teachings of the best monk in the West, it could be said that these were truly days of disappointment and lamentation.

Why does the Emperor not give us teachings?

Is it because we were lacking?

Or was it because they were a branch of an enemy country and not the main palace?

Of course, Emperor Geotap doesn't know.

He just sits cross-legged and quietly radiates a halo. For a great master, isn't he only working towards his own nirvana?

Runlin, the leader of the Blood Thunder Temple, couldn't help but feel sad.

"[Your Majesty, was there no other word from the palace?]"

Although it was expressed as a word, it was asking if there was no support.

It was an indirect way to avoid being rude to the most powerful and unmanned person in the West, who was directly asking if there was any more support.

Then, Emperor Geotap opened his eyes halfway and asked solemnly.

"[Hey, what were you so afraid of?]"

"[It bothers me that those wicked Zhongyuan cultists were still silent. I wonder if they were planning to gather warriors from the mainland and attack……]"

"[There was no such thing. If Zhongyuan' seers were engaging in suspicious activities, I will be able to detect them immediately with my supernatural powers. Do not be afraid.]"

Of course, that supernatural power wasn't working at all.

Of course, Emperor Geotap also had his own reasons for being confident.

First of all, the Blood Thunder Clan was unaware that the operations it was carrying out in Hanam County, south of Qinghae Province, had been exposed.

So, at best, the justification given by the Blood Thunder Demon was to get rid of my pro-Zhongyuan faction, the traitorous scum, and to clear out a few villages of scum who had forgotten their roots.

Since they lost the monster, they will use that as an excuse to invade.

This was actually a good thing.

The monster probably thinks that the current Blood Thunder Sound Temple has only one master, the head monk, and that it was an uninhabited mountain.

The same goes for Kunlun, who hears the words of the monster.

And since there were no people who calculated as much as the Jeongpa bastards, they wouldn't borrow the power of the Wulin Alliance to attack a single Blood Thunder Demon who had lost all his masters.

There was also the issue of the Kunlun faction's reputation, and isn't support ultimately an act of indebtedness?

Above all else.

Emperor Geotap opens his telescope and sees the figure of a woman lying dead under the bed.

Even if support was requested, at least one combat unit will be dispatched.

But was dispatching a combat team an ordinary thing?

In order to gather people from the Wulin Alliance and coordinate their movements to Qinghae, it was natural that people and goods would have to move back and forth.

And wouldn't the thing in the shape of a woman under the bed, a dirty and ugly monster that only had the appearance of a human, have the strange ability to communicate across Zhongyuan with a voice that could travel a thousand miles?

From the gathering of the reinforcements to their departure, if such a sight was caught, it was the Emperor of the Tower who would hear the news immediately.

But Runlin was restless.

The Giant Pagoda Emperor clicked his tongue and said.

"[I will tell you my future first, so listen and put away your fear.]"

The evil bandits disguised as Taoist priests, the horsemen of Kunlun, will dare to invade the sacred mountain.

They do not know the true power of the Western people, so they will just laugh and wave their flags excitedly.

"[This was because they were greedy and want to plunder the sacred mountain and gain wealth. The people of Zhongyuan were all beasts with parents of dogs and pigs, trash with the blood of thieves flowing in their veins, a lump of filth worse than trash, a harmful evil that must be eradicated from the world.]"

Since only this part exuded such deep hatred, I couldn't even guess what kind of grudge he held against the people of Zhongyuan.

"[But here was the throne. How many times can a Kunlun master try? If I swing my staff, one will die, and if I extend my palm, I will strike down another.]"

The Giant Pagoda Emperor shows a gloomy smile.

It was a smile that smelled like blood.

"[At that very moment, those scoundrels will charge first and shed blood alongside the scum of Zhongyuan. The sin of daring to disturb the sacred temple of the Holy Mountain will be repaid with the blood they shed.]"

Runlin also gives a bitter smile.

Aren't you talking about those lowlifes brought by the Great Pagoda Emperor, who have no respect for monks or even for Buddha?

You said that everything was useful, so if you use it for that purpose, I can tolerate your current rudeness.

"[So, those Zhongyuan people, trembling with fear and panic, will drop their weapons and try to flee. At that moment, the main force of your Blood Thunder Demon Masters will rush in and slaughter them all. Then, we will advance to Mount Ilwol, set fire to the Kunlun Taoist temple, liberate Xinying, and make known to the whole world the great will of our Xizang people.]"

"[Oh……!]"

"[It seems to me that I can already hear the cries of our people in Xinying, rejoicing at their liberation from oppression. Can't you hear it?]"

At that, Runlin shuddered.

Indeed, you were seeing such a future!

This can't be happening…!

Strong! Our chief was strong!

He was indeed the Giant Pagoda Emperor!

"[No! I, the unworthy disciple, was blinded and foolish, and trembled with delusion and anxiety. The teachings given by the Emperor, like the bright light of Vairochana Buddha, illuminated my mind as well.]"

As he spoke, Runlin's expression remained unshaken, and the anxiety he had shown until now was nowhere to be found.

Because the glorious victory that was about to happen, the future so clear, was already guaranteed.

maybe.
