\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (19)}

It was a miserable sight of the greatest master of Xizang.

His head was broken and bleeding, one eye was swollen and unable to open, and his nose was bent vertically and was oozing blood.

On the other hand, the hem of the clothes was in tatters, with not a single intact spot, revealing the raw flesh underneath.

The three Hyeon-gyeong masters already sheathed their swords.

Of course, Monk Wunue did not use a sword, but Ximen Surin and Nan-Gongdaero had put away their swords and were swinging them with their scabbards on.

Thanks to that, there was only the sound of beating.

The Giant Pagoda Emperor doesn't know what to do and just tries to escape in confusion after being hit.

But he's already limping from a leg injury and three fingers were dangling, so, well, that little punk was really the best.

To anyone who sees it, it might look like the three of them were harassing one person and committing a merciless assault.

Of course, it looks that way to me too.

But Qing realized the elders' intentions.

Because they were pushing to capture them alive, not to kill them.

Perhaps after destroying his limbs, they would break his dantian and locked him in the Repentance Room.

Even the Giant Pagoda Emperor knew about the intention and was desperately guarding his own two feet.

He was desperately trying to block the attacks directed at his legs by flailing his arms, so much he looked like he was going crazy!

Oops, now he had one of his arms broken.

It was a very refreshing and heart-opening sight.

\textit{We won, but…}

\textit{Hmm, Master, is this okay?}

Something like a high-level martial arts feast performed by the masters of the present world.

Oh, Master, I won!

Ah. You're going to win with a stick…

Even as the three of them beat up one person, Ximen Surin maintains her elegant demeanor while quietly carrying her backpack behind her back.

It may be a bit irreverent, but isn't that why Master achieved great success in swordsmanship?

Why, you have repeatedly said that the more female a warrior is, the more she should be a role model with dignity and beauty.

Even now, in the midst of this brutal beating, aren't you still displaying the image of a noble beauty?

The focus was on Qing police officers.

Because it looks like he'll be dragged here with broken limbs soon.

Could this be the hundreds, thousands, or even tens of thousands of red lights?

The unknown light shining on the screen was just a dull yellow, a cloudy afternoon, and the passage of time was impossible to tell, making the moment seem like an eternity.

The lamas of Blood Thunder Temple simply run and run, crossing the interior of the temple.

Now, I can't remember where I came from, and when I come to my senses, I realize that everyone has disappeared and I am left panting alone.

"[Master? Jutan? Jaom Death Penalty?]"

The lama chants as if giving advice.

It was because of some instinct, some fear that I shouldn't make a loud noise.

Suddenly, the son-in-law was quiet, a perfect silence without any sound.

Since there was no sound, only the sound I make resonates loudly.

For the first time in his life, the lama realized that his breathing was so loud and that his heart was making such a loud roar.

Suddenly, the son-in-law gets angry.

A feeling that can only be expressed in that way.

A certain sixth sense, an infinite sense of foreboding that seeps into the upper body, conveys a strong sense of foreboding.

Something scary was coming! Something harmful was coming!

Your end was coming!

And then, creak!

"Ahhh!!"

The lama screams and stretches out his head.

As the bloodsucker flashes across, he opens the door and strikes the chest of the intruder who came in.

A foul smell that makes him fall down.

A boiling voice flows out.

"[S, Master? How……]"

Only then did the lama realize the identity of the uninvited guest.

Aren't you one of the youngest disciples who still has a long way to go in terms of achievements?

"[What have I, what have I done!?]"

But he was a disciple with a sunken chest.

"[Cough!]"

Soon, with a final cough, blood splashes down the lama's face.

The appearance of a disciple who was drooping.

The lama looks down at the sight blankly.

That was the moment.

Ding ding!! All the doors of the Red Light Hall open at once with a loud noise.

And the sight of lamas appearing one by one at each door.

Among them, Runrin was startled by the sight of the lama sitting down, hugging the injured person, and runs towards him.

"[What the heck! What was going on! Who dares!]"

"[That, that. The disciple, the disciple.]"

The lama closed his eyes tightly.

It was an accident, just an unfortunate accident.

"[……I don't know.]"

"[How, how could this be……]"

It was when Runlin was chanting with a miserable expression.

Suddenly, thump thump thump… …!

From a very far away place, a sound like a sheet of iron collapsing can be heard in rapid succession.

The lamas' expressions harden.

Because the sound was getting closer quickly.

And because they were coming from all directions at once.

"[Master! What should we do…!]"

A lama grabs Runrin by the collar.

It was an incredibly irreverent thing, but the hand he held so desperately represented the desperation of the lama.

But Runlin has no answer to give.

With the sounds coming from all directions, where on earth can you run to?

Empty, empty, empty!!

Before I knew it, the sound was getting closer.

The lamas, without realizing it, gathered together in a hesitant manner in the farthest place from the sound, in the middle of the red light hall, in the farthest place from all directions.

And then thud thud thud!! Thud!!! Thud!!!!

The final roar resonates just around the corner.

The sound of the red light ringing in the room across from me.

The moment when the lamas swallow their saliva.

Creak… …!

With the sound of wood twisting, the four-sided sliding door walls of the red lighthouse tilt back.

The lamas, huddled together and holding each other, were shown the scene behind the collapsing wall.

A large auditorium in a circular shape.

It was an infinite viewing platform that slopes endlessly upwards and continues to the darkness at the end of the field of vision.

And the translucent human figures that fill it all, each with their clear eyes wide open, look down at the lamas and direct their lusterless, dead eyes at them.

Thud!!

The sound of the wall finally collapsing completely.

And on one side, in the direction where the main Buddha of Jeokgwangjeon stood, there was a huge barrier, and a huge human figure leaning against it.

It was a giant wearing a judge's hat.

As soon as the lamas recognize it, they realize its true identity.

King Yama. The Judge of the Underworld.

"[I will pass the judgment!]"

A giant delivered a cold sentence in a voice like thunder.

"[Let the ten thousand years of the light Hell, the ten thousand years of the black Hell, the ten thousand years of the combination Hell, the ten thousand years of the circular Hell, the ten thousand years of the great circular Hell, the ten thousand years of the first heat Hell, the ten thousand years of the great first Hell, the ten thousand years of the father Hell, make this circle turn ten thousand times in one cycle!]"

This refers to the worst hell, the Eightfold Hell, located in the deepest part of the Buddha's hells.

It was a terrible punishment to be tortured in the eight hells, alternating ten thousand years each, ten thousand times.

The lamas flopped down on the ground.

As a disciple of Buddha, they knew how harsh this punishment is.

The only one who remained standing was the head monk, Runrin, and even with trembling knees, he bravely looked up at the judge of the underworld.

"[Oh, King Yama! There must be something, something wrong! We are practitioners who practice the Dharma for the salvation of all people! How can you condemn us to hell!]"

At that, Yeomra's expression distorted, and a voice full of hatred resonated.

'Anyone who kills an innocent person will be executed!'

'Those who preach evil sermons will be punished by the Black Monk!'

'He killed to satisfy his greed, so he was a murderer!'

'He killed to fill his own stomach, so what a disaster!'

'You deceived and harmed others, so you were in big trouble!'

'And you, lama, who impersonated Buddha and insulted him!'

"[When did Buddha ever teach you to kill your own people? Are you asking me because you don't know your own sins? Your sins have already been testified in this place!]"

"[We just-]"

"[That lama killed me! Because I followed the customs of Zhongyuan!]"

A desperate cry cuts off Runlin's words.

"[That bastard gathered the robbers and ordered murder! My body was still frozen in the cold mountains and rivers, unable to close its eyes!]"

"[That guy was-]" "[That evil-]" "[That guy-]"

From the endlessly stretching stands, whitish figures rise and stretch out their fingers.

Runlin's expression hardens.

"[How pathetic! While alive you committed all evil deeds, always opening your mouths and boasting to each other for going to hell. So how can you refuse to stand before the judgment, feeling unjustly wronged?]"

"[We, we just……]"

Runlin trailed off.

'If I don't go to hell, who will?'

'For the sake of the long-cherished desire of Xijang people, I will willingly take the lead and open the world of slaughter.'

Suddenly, I feel like I can hear the voice I used to say from within me.

Suddenly, Runrin lowered his head at the smell of blood that was thick and thick, and before he knew it, his hands were covered in blood and had taken on an ugly appearance.

Runlin's expression gradually disappears.

That was when.

"[Your sins are not yours alone!]"

A stern voice.

Runlin raises his head.

A heart that feels so ominous and falling.

Above all, I had a premonition that terrible words would follow.

"[Your greatest sin was preaching sin with false teachings. Your people have distorted and defiled the Buddha's will. Therefore, every single one of your people, without exception, will suffer in hell! It was your sin, your whispering of evil deeds, that has led people to sin! Because of you!]"

"[Oh, King Yama! No! How, how can you blame our sins on our own people-]"

"[Because you taught that murder was justified, that plunder was good, and that all sins committed through aggression were justified.]"

"[Then please just hold us accountable for our sins-]"

"[No one can atone for other's sin! Your people will never be reborn as humans again, but will be reincarnated as animals, suffering eternally! Thus, your people will disappear from the cycles, becoming a stern warning to all people about the severity of the laws of the afterlife!]"

"[No! We'll take that burden for our peop-]"

That was the moment.

Suddenly, a strange light pours into the dark underworld, and an ugly color that has never existed in the world begins to fill the surroundings.

A terrible celestial body that has suddenly filled the sky.

It was the sight of a monstrous star with a gigantic, empty eye, swirling in all directions with tens of thousands of ominous colors that had never existed in the world.

"[What! Who dares interfere with the judgement of the Underworld! You rascal, no, no! Quickly! Send the sinners to hell!]"

It was an urgent order from King Yama.

Spirits with chicken heads poured down from all directions.

As they all rushed towards the lamas, closing the distance at once-

At that moment.

The sound of water drops falling.

A single drop of ominous light fell at the feet of the lamas.

And that moment.

The silver lake expands at an infinite speed, pushing the landscape of the underworld in all directions.

The scenery of the afterlife disappeared in an instant.

Only the angry voice of the King of Hell echoed.

"[The judgment of you heinous sinners has already been made. This is only a brief respite, and cannot change a future already determined…]"

The world was reflected in the eyes of the lamas.

Just a silver horizon with nothing else.

At that moment, the world's most evil gaze and most sinister voice penetrate directly into the heads of the lamas.

[You are a sacrifice offered to me.]

[Because of you I have extended my territory to the Brahma world, and the deal has already been made.]

A certain scene burrowed into their mind.

The Heavenly Emperor of the Tower cried out with a crooked smile, 'O evil spirit, I offer these vile things as a sacrifice. Please lend me your strength and reveal them to the world as the great bloody and cruel demon.'

And the whispers of the evil spirits continue.

[Now you are mine.]

[It would be better to survive desperately]

[After your death, there is only hell waiting for you.]

[Now, struggle.]

At the same time, the world begins to crumble.

The door that stands tall in the distance shines with a dazzling light.

The lamas run out at once.

With a look of despair more than anyone else in the world, and also filled with desperation.
