\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (5)}

The time in which Qing exists was an ancient, primitive era before the establishment of a full-fledged human civilization, a time in which inferior primitive people lived.

The fact that the level of civilization, individual perception, ideas, and social status were not significantly different from those of similar human apes proves this.

Even communication was like that.

Unlike Qing homeland, where information could be exchanged without time lag anywhere in the world, communication in this era relies on human footsteps.

However, these ancient primitive people also had a secret weapon of their own: the cutting-edge technology that allowed them to fly through the sky on their own.

Its name is the carrier pigeon!

If you catch a smart pigeon, raise it with care from a young age, and raise it with care, even the most stupid bird will remember its home.

So, they take them out of the house and first release them in distant places, first 10 li, then 20 li, then 30 li, and train them to return home.

It's closer to releasing animals than training, and it's more like weeding out the bad guys from the start.

Among them, only the pigeons that unconditionally return home were qualified to become the best delivery riders in Zhongyuan, the carrier pigeons.

If you release these elite pigeons from afar, they will fly high into the sky and return to their home. This was the principle by which letters can fly on their own.

However, it was not widely used.

First of all, the cost of training pigeons were not small.

And because of the limitations of a stupid bird's brain, if you leave it in a foreign land for a long time, it tends to forget where its home is.

Besides, Zhongyuan people eat pigeons!

So, even if a pigeon was a near-spiritual creature that understands human speech and can fly ten thousand miles to return home, it was nothing more than a meal for the hungry people of Zhongyuan.

So, in fact, the reliability of the carrier pigeons were very low compared to the cost and difficulty involved.

Because it was urgent and critical news, they even use a messenger to send it, but the problem was that there was no certainty that it will arrive.

But, in times of emergency, you have no choice but to use it.

Just in case, send someone even if it's late.

What was lacking in credibility was made up for with numbers.

The messenger bird, which must fly at least ten times to deliver a single message, barely manages to arrive.

So let's go back in time to ten days ago.

On the twenty-fifth day of December, twenty pigeons flew from Kunlun Mountain and each set out on their own adventure.

Forgetting home or forgetting the way home.

Or you can fall for the temptation of a beautiful, well-fed pigeon and become a pigeon father.

Being eaten by hawks, owls, and wild cats.

The most dangerous enemy were Zhongyuan people.

The ferocious appetite of Zhongyuan people, who eat everything with wings without exception, was too cruel for a single flying creature.

And Foodduck, out of twenty, only one lands in the Wulin Alliance's Jeonseo Pavilion.

After that, there was another one that arrived late after playing, but the world only remembers the first place, so no one paid any attention and just gathered peacefully to peck at it until it was discovered.

This was the brilliant technology of primitive people!

They were the secretaries of the secret book, the secret masters, and the secret engineers who immediately opened the secret book and deciphered the secret code.

That was the nightmare of the Western world, and the biggest obstacle was the gluttony of Zhongyuan people. If it wasn't encrypted, wouldn't the contents of the Western text spread throughout the world?

"The Xizang's invasion is imminent. I request priority support from a high-ranking expert. Details will be relayed by a disciple who arrives later. - Kunlun Sect Leader."

This was the greatness of the carrier pigeons.

The carrier pigeons could travel from Qinghae Ilwolsan to Wulin Alliance headquarter in Kaifeng in just two days, boasting a speed that was literally like lightning.

It's expensive, unreliable, and has such a low transmission capacity that I can't even write a few words about it!

In the first place, how big can a messenger be that was not in the way when hung on a pigeon's leg?

It was also a message that became very urgent thanks to the reduced number of characters.

The cryptographer urgently relays this shocking news to the Meng Zhou Dynasty.

"What!? The Xizang's bastards? These guys, it's not even the New Year yet…! I need to get their cooperation right now!"

Of course, that doesn't mean all the masters of the Jungpa martial arts world can leave their posts.

First, send the experts in the nearby area first, and then request that those far away be reassigned and on standby to monitor the situation and prepare for dispatch.

To be exact, he requested support from Shaolin, Divine Maiden Sect, and Nan-Gong Sega.

The leader of the martial arts world cannot leave his post hastily, and if the Murong family head comes down to Anhui for a while.

And for the dot-splash faction, well, I'll send someone to let them know, but it would be better for the flash sword to keep its place in the dot-splash faction…

It was just three days before the New Year.

Thanks to this, the poor Jeonseo-gak members were dispatched to all over the country just before the New Year.

Unfortunately, the members of Jeonseo-gak were unable to spend the one day the new year was over, eating dumplings with their families and watching the fireworks.

But who can you blame?

Of course, you should blame those Xizangs.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Despite the end of his prison experience, Qing was still bored and lonely.

Why was everyone suddenly so passionate about martial arts training?

No, since when did you start training like this, almost dying?

I felt this before, but the characteristic of kids who were bad at studying was that they study when others were playing and play when others were studying.

During the Lunar New Year holiday, you should go sightseeing in the city, visit the night market, and rob street vendors, inns, and bars.

Well, this one needs some training though.

So, Qing was bored.

If it's going to be like this, I should have just extended the prison term and continued watching the prisoners' antics.

It was truly a feast of talent.

It was quite amusing to have a fight where they would pull out each other's nose hairs and whoever sheds tears first would lose.

The cheek-slapping contest eventually devolved into a full-blown emotional fight, with cooking taking a backseat, and it was a match worth watching.

The stone fist's massage was also at a level where it could block the attack with a force of about 50 …

It would be a little strange for the disappeared summer to reappear.

If I take off my face mask and go barefaced, will it be okay? Won't they not recognize me?

Just loafing around like that.

To be exact, I did increase my internal energy level through the accumulation process, but in reality, accumulation was also semi-automatic, so my mind was filled with other thoughts and it was incredibly boring.

So it's the tenth day of the new year.

Today, too, Qing sat cross-legged and lost in thought.

Even if it was just a little bit, we would go out and play together.

However, since the training center only opens its doors once every ten days, there was no reason to go and visit even if you want to.

Of course, I could get it out if I tried, but what would that do to me?

You'll just end up being a reckless younger sibling who interferes with your sister's training.

There was a unique characteristic of Mansangyeoilsingong.

When the fortune telling was done, a soft golden glow appears as a halo, shining like a ray of light, and the corners of the mouth naturally resemble the Buddha's mysterious smile, resembling the empty and benevolent expression of the main Buddha.

In Cheonchuk and Xijang, martial arts were one of the means of governance, so it could be a function that was intentionally added, or it could just be a side effect.

Sitting there in meditation, with a faint smile on his face like a monk who has attained enlightenment, Qing thought.

\textit{Hmm, I want to touch Yi-mei breasts.}

\textit{Hey. My heart is pounding. Her breasts ss mine, so how can I not even touch it?}

\textit{There is no substitute for the fullness that fills those hands and the softness that flows between the fingers.}

If someone were to look into her inner thoughts, they might click their tongue and say, 'What a truly wicked Buddha, shouldn't she be called an obscene Buddha?'

But how can a person clearly read another person's mind?

It was a realm not permitted to humans, so even if one were a superhuman or a master of the realm of the supernatural, with outstanding martial arts skills and a grasp of the mystical, it would be impossible.

That is, even to the masters of the Profound Realm, Qing's appearance was lonely and strange, as if she was absorbed in something and wandering in enlightenment.

So, even though it was Kunlun, the mind of Ximen Surin, who ran to Kunlun in one go and flew through the sky out of concern for his disciples staying there, cannot help but be very satisfied.

Suddenly, she felt sonmething lacking.

To be exact, what's inside was lacking.

Her already vigorous digestion had become even more active due to the effects of the raw heart, so she's feeling hungry even though there's still plenty of time left until dinner.

Qing's eyes widened at the thought of being released.

The moment she thought she should look for a snack, her master was smiling happily in front of her.

"Oh, Master!"

"Come, do you understand now?"

"Had you call me, I would have greeted you first. Why did you keep waiting so long?"

Then Ximen Surin smiles.

"You were so absorbed that even outsiders wouldn't notice. Seeing Disciple's immersion made me lose track of time. So, you seem to be feeling better now. Did anything happen?"

"Hehe, what could be the big deal? This disciple is now a respectable master."

Qing slowly approached and very naturally placed his small head on Ximen Surin's thigh.

But this was not the kind of thing a disciple should do when meeting his master.

But what's scarier than boiling water was water that boiled slowly, and Ximen Surin has already seen too many of her ignorant disciples' antics.

\textit{When the child was at Transcendent Realm, she was truly starving for affection, so I have no choice but to hold her.}

\textit{As soon as she entered the Unrestrained Realm, I became so accustomed to it that I naturally started stroking her hair.}

"Yes, I saw Disciple's aura. The golden quivering energy was no ordinary divine skill. Have you picked up a new martial art?"

"Yes. It's called Mansangyeoilsingong."

"Oh. This is a divine skill that is beyond compare. Yes. You've picked up something wonderful."

Even when a disciple leaves, he was used to knights picking up other people's divine skills, so a lap pillow would not be considered strange.

"Actually, this disciple met a strange monk on my way to Kunlun. Oh, do you know the Strange Monk? Oh, you know the Strange Monk. So…"

Qing, who was bored, even forgot about her hunger and started talking about her journey.

Ximen Surin had already heard the whole story from Tian Feizi and even seen the face of the Strange Monk.

She was about to hear the same story again, and then she suddenly realized, "Oh no."

\textit{How could this girl not fear her teacher and dare to lie down on my knees? Come to think of it, she's even haven't pay a proper greeting.}

\textit{Where on earth did it all go wrong?}

Now, it was Ximen Surin who was like, "Oh my."

But she let it slide because her disciple was a bit special.

Is Mansangyeoilsingong an ordinary divine technique?

Ximen Surin was even more delighted to hear that this time it was not obtained through some hidden means, but in return for cooperation.

This was exactly how you ruin a child's manners.

"Oh, Master. Would you like to go to the night market? It's the Lunar New Year, so there's a big night market in Xinying, but come to think of it, I don't remember ever going for a walk with Master. 'Master'\footnote{師父; Shifu} and 'parents'\footnote{父母; Fumu; lit. 'father mother'} share the same Chinese character, yet how can there be such miserable unfilial conduct in the world? Hehe, this disciple's negligence is truly shameful, so I will take this opportunity to show you my utmost respect."

Even before she went to the Hanlin Academy, she was quite good at reading and writing.

Although it's not like a girl who can read and write would lie down on her master's thigh.

"Yes. Let's see the virtue of a mature disciple. Even I have never walked the land of Xinying before, so if you're willing to guide me, I'll gladly take a walk."

Ximen Surin was now beginning to have thicker brows on her eyes.