\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (13)}

The lamas of the Blood Thunder Temple have settled on the southern ridge of the Arabdal Mountains.

It was the twentieth day of the first month in Zhongyuan calendar.

Even in the middle of winter, there was no such thing as a winter like this, so we have to stay out overnight until the enemy comes.

Still, the morale of the lamas of the Blood Thunder Temple was not bad.

Because I had no doubt that the Emperor of the Tower would shatter the oppressors of that detestable invader nation.

but.

"What were you guys doing! Can't you turn it off right now!?"

When the night gets dark and the lights go out, Runlin looks at the llamas and shouts in horror.

Well, isn't the winter sky clear, cloudless, and the bright moon shining brightly?

When the smoke rises, it was no joke; a white streak can be seen reaching the sky from a hundred miles away.

"[Master? But what will we do with this cold if we don't light a fire?]"

"[Ahem. But there's nothing we can do. Aren't the enemies coming? If the Kunlun horse-nosed bastards see this smoke and head here instead of to the headquarters, won't the Master's arrangements be disrupted?]"

Teacher was a title used by monks in the preface to address high-ranking monks.

The word Lama, which originally referred to the monks of the West, means teacher in the West's language.

And the great master, as the preface says, was called the Dalai Lama.

Anyway.

"[Then what should we do?]"

"[It can't be helped. If we gather together, share our body heat, cover ourselves with thick blankets, and practice good weather, we can ward off the cold.]"

The llamas became depressed.

By the way, there was a saying in Qinghae Jokjo that goes, "A person in Xijang takes a bath three times in his life."

When you were born, when you get married, when you die.

It's a joke, but in reality, it's not easy to get water in the West Sea.

Moreover, since it was a region with strong winds and cold weather throughout the year, it was easy to get sick if your body gets wet.

So it's true that I can't take a bath.

It was so special that there was even a separate bathing festival that takes place in mid-July, the warmest month of the year.

"[Master, then dead……]"

"[You guys, even as the fate of liberation hangs in the balance, do you, the so-called lamas, care about your own comfort? Since when have you been boiling champas like that?"

The llamas became more and more depressed.

How special was hot food on a cold day?

But since I can't make a fire, it's all in vain.

Now, aren't we supposed to spend the night shivering and crying, smelling each other's stench and chewing on raw barley flour?

But somehow.

But it's not like I can refuse, so I have to curse if you want and hug if you want.

First night.

The morale of the once high-ranking lamas plummeted.

however.

The llamas' troubles did not end here.

Ten days later, at the beginning of February.

In just ten days, the llamas had swollen cheeks.

Well, I sleep alternately at night and during the day, taking naps.

The night was cold and the smell was terrible.

I didn't even want to look at that damn barley anymore.

If Amukhaprap had seen this, he would have clicked his tongue.

The Vajrayana monks should be practicing virtue among sentient beings, sleeping on the roadside and begging for food, but they were whining like children because they were only offered good beds and good meals.

It was a bitter remark made while he was also receiving good food and a good bed.

Thanks to that, he didn't have much popularity even within the Blood Thunder Society.

Anyway, as the lamas' suffering continues, when on earth will the Kunlun sect warriors arrive?

The Kunlun sect's procession, which assists the monster's revenge, has now traveled only six hundred li.

It was an incredibly slow pace for a procession of Kunlun Sect elites, each of whom was at or above the peak of their power.

Are the Kunlun warriors being lazy?

Of course not.

Even the Kunlun sect warriors had no choice.

The original plan was to head straight to Hyulryeumsa Temple along a straight road of 1,100 li.

This plan was designed on the premise that they would stop at large and small villages along the way to provide food and lodging.

however.

"Huh. Amitabha Buddha……"

Ambassador Wunue chants a prayer in sorrow.

The corpses that had been left unattended for a long time, the tents that had collapsed due to lack of care, the buildings that had grown cold.

The Vajrayana monks who set out to deal with the Amukhaprap stopped by each village of the Jang tribe and provided opportunities to accumulate merit.

However, the village of Jangjok, where he arrived to do such meritorious deeds, was already seriously polluted and only contained Hangans.

In fact, it has been hundreds of years since the land of Qinghai fell into the hands of Zhongyuan.

How can one maintain customs that were different from those of Zhongyuan after living for hundreds of years?

The purity they speak of was nonsense to begin with.

"I think we should follow the road. Even if they were crazy, they wouldn't have been able to annihilate the city where the Chisso was installed."

"Huh."

It was difficult to imagine that there will remain villages that will receive supplies intermittently in the future.

Even if there were still people left, aren't they just extreme people who agree with the absurd nonsense of the Blood Thunder Demon?

So, the shortest distance of 1,100 ri had no choice but to change to a journey along the national road of 1,400 ri.

Even when a fully developed city appeared, we had to rest and stay overnight while it was still daylight, so the time just kept getting longer.

"Fish cake, were you okay?"

"There has never been a time when the Great One was as miserable as now. Even if I had a hundred mouths, all I could say was regret. These bald, fatherless men should be roasted in the eternal fires of hell."

A sorrow wells up in the sunken eye sockets of Amukhaprap as he looks at the fallen tent.

Qing just tapped my shoulder.

"Hmm."

The sight of the thin chest of the Amukhaprap sinking down was like a silent sigh.

Five days later, on the thirteenth day of the second lunar month.

The last city to reach Ahaprapdalhaptaeksan at a speed of one and a half days was Gyeokimok-hyeon.

Finally, we each have a drink and some good food, get some rest, and then start the final battle inspection from dawn.

We spread out the examination and ran a rehearsal.

Each person packs five days' worth of food, checks their packs, and forms a line again.

As the full moon approaches and night breaks, we move through the night to the foot of the northern ridge.

After eating breakfast and getting some sleep, we finally form our formation while eating frozen rice balls for lunch.

Even though the three best martial artists were together, they all look nervous before the actual battle, and an ominous war atmosphere hangs over them.

So, let's go.

Qing took his place at the very front of the line.

He was a master of the flower world, and it was right for him to stay by his master's side.

As we cross the ridge, a white and blue temple in the style of a Buddhist temple comes into view on the opposite mountainside.

Unlike the mountains of the central plains, there were almost no trees, and the western mountains were made up of sparse shrubs that only reach waist level.

Qing's human-transcendent vision did not miss the figure standing proudly in front of the mountain gate of the Blood Thunder Temple on the other side.

Of course, even if it wasn't transcendental, it would have been possible to know that someone was standing there.

First of all, the hair was shiny.

"Who was that guy? Is that guy the head priest?"

"Strange. That little bastard doesn't look like that. He's seriously underweight. He must have eaten his father and mother to achieve his impressive appearance."

"For something like that, he's standing there blocking the door with such confidence, like a leader. Ah, let's go in."

The fact that the enemy was visible here meant that the punitive force was clearly visible from the other side.

Within, thump …!

It was a loud bell sound that echoed across the quiet stone mountain.

The original bell that announced an intrusion had no sound box and was made of thin iron plates joined together. It produced a noise that was enough to tear the eardrums.

The same goes for the Blood Thunder Temple, where a loud, crackling sound echoes throughout the winter mountains, as if trying to wake up the animals from hibernation.

If the enemy hadn't noticed, there was no need to rush when the bell was ringing like this.

Moreover, the Blood Thunder Demon didn't close the main gate, which was as strong as a castle gate, but left it open.

As if to say, "Come in if you want to come in."

The basic defense was to lock the door and lay traps behind the wall.

The Kunlun punitive force advances in a strict formation.

Since the rocky mountains of Qinghae were wide open on all sides, it was not possible to see the enemy lying in ambush, and even if they did, there were three high-ranking officers in Hyeon-gyeong, so they will not be able to detect their presence.

In fact, no matter what I prepared, I don't think I could stop the power of the three Hyeon-gyeongs.

So, they changed their formation, with the experts on the outside and the slightly lower-level, early-to-mid-level players on the inside, and finally passed through the main gate of the Blood Thunder Temple.

The vast courtyard of Hyeolryeumsa Temple, with dozens of pagodas as tall as a person lined up on a bed of blue stones.

In front of the main building, Daeungjeon, which was the largest building along the wide brick road in the center, a lama stands proudly on two feet, smiling for some reason.

And then he opens his mouth-

-The horses of Kunlun were finally setting foot on the limbs!

It was a technique of the Six-Hap Battle, a noble sound that could not be identified from the four directions, above and below, and six directions.

It also meant that Rama's realm had reached the state of enlightenment.

-Let's see. Hwagyeong two, four, six, eight! Haha, you guys were full of confidence. With eight Hwagyeong warriors, you dare to invade the sacred land of the West Jang with such arrogance!

In fact, there were only three Hwagyeong from the Kunlun faction who went on the expedition.

There were three Kunlun Flower Mirror masters in the punitive force.

Add the green and yellow monsters to that and it's five.

Of the eight people mentioned by Emperor Geotap, three were empty.

But Emperor Geotap also had his own reasons.

Because the masters of Hyeon-gyeong were able to discern the realm up to the peak.

So, when you can't read the opponent's state of mind, you can just call it a state of mind.

Of course, he may be a better expert than Hwagyeong.

But when it comes to Hyun-kyung, most people know each other by face, so even if there was a hidden hermit, wouldn't it be said that Hyun-kyung was not over twenty years old under the sky?

On the one hand, I was secretly impressed.

When it comes to the Kunlun faction, isn't it considered the weakest among the old factions, along with Qingcheng and Ami factions?

Even so, the number of mobilized firefighters was six, excluding that traitor and that damned Cheonhwageom!

It's a power that's hard to imagine for a single sect.

Indeed, the old school.

The exploiters who ruled Zhongyuan for a long time!

How much effort must it take to have that much power?

"Kuuuuuu……"

The Giant Pagoda Emperor can't hold back his laughter.

And isn't this the moment when one of those old guard was falling?

And I did it with my own hands!

-Kuhehe, I am the Emperor of the Tower.

One, two, three for him.

"The Great Tower Emperor!" "The Greatest General!"

The green and yellow monks shouted together.

To be exact, only two people shouted.

How could someone like Chief Xijang Jeil know someone like that if they weren't a Chief Xijang person?

Qing felt like he had to pretend to know, but in reality, only Amukhaprap knew the weight of that name.

Qing scratched his head.

I guess now isn't the time to pretend to know.

As the Kunlun sect's martial artists were in an uproar over the unidentified Hyeon-gyeong master, the moment Master Wunue was about to take a step forward-

"You vile and wicked Han Chinese bastards insist on bringing your foul, stinking bodies into the holy mountain. This was a grave sin that cannot be repaid even by ten thousand deaths!"

The excited Emperor Geotap's Yukhapjeonseong stops Master Wunue from speaking.

It was at that moment that Ambassador Wunue wiggled his eyebrows and took a deep breath.

A gust of wind slapped Wunue's back, and when he turned around, Ximen Surin shook her head with a pitiful expression.

Let's see what he says.

Ambassador Wunue just exhaled.

Actually, I'm also curious about Wunue.

Without even knowing it, Emperor Geotap was excited.

"Aren't you Han Chinese bastards originally the offspring of slaves? You scum who licked the feet of the Mongol people and lived off of them, so you've gotten lucky and taken control of the world. Your evil deeds were all the result of your base nature."

Then Qing poked the monster's side!

'No, why were you nodding?'

"The author was a vicious villain. But his words were infallible. Right and wrong were inescapable truths, and even the great truth of oneself cannot be denied."

"You're funny. Emperor Dalai Lama said Dalai wasn't the words of the Emperor, but of the barbarians. Then, weren't you also just a lackey under the barbarians?"

By the way, barbarian was a derogatory term for Mongols.

Nowadays, it was used as a word to encompass all kinds of foreign ethnic groups in the border regions, but the original barbarians were those Mongols, the homeland of Qing Dynasty, and in that sense, only the Mongols were referred to.

So, Qing was right.

The Mongols were truly one of the world's greatest powers, conquering not only East Asia but also other continents.

Except for the black-skinned, no people in the world can escape the warm history of the Mongols.

'Just one more word, for even you, the brave one, cannot endure any more insults.'

'Huh. They say it hurts if it's true.'

-Go! Who dares to speak in front of the Emperor?

"Who was the emperor? Isn't it embarrassing to call yourself the emperor? And what kind of monk was the emperor? Are you above some Buddha or something?"

Qing's specialty was pretending to talk to himself while scratching.

It was a sound that everyone could hear, so even the Kunlun School burst out in laughter.

The Emperor of the Tower explodes with his murderous intent.

"Anyway, you're not a bastard, were you-."

Then, Qing suddenly shut his mouth with a very pale face.

However, it's not because I'm afraid of living.

Because the master glared at me.

Miss, the master was here.

Qing slowly puts her hands together and belatedly assumes a cautious posture.

But it was already too late, as Ximen Surin's displeased gaze showed no sign of abating.

Oh, I think it's Jo Jin.

Qing belatedly regrets it and shrinks her neck.

Then, the Giant Pagoda Emperor, who knew that he was scared by my murderous intent, smiled in satisfaction.