\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Sect (1)}

The operating policy of the Repentance Hall was one of complete neglect.

It means that there was nothing to be ordered about.

This was much more severe than forced labor.

If you're stuck with the same people for ten, twenty, thirty years without ever stepping outside, you'll end up with nothing to say to each other.

Even if you try to have a conversation in the first place, there needs to be something new to talk about, right?

I woke up, ate, and went to sleep.

Because I was just wasting time for a long time without any stimulation.

Didn't they even castrate him?

I could have spent some time telling dirty stories, which was a specialty of men, or at least comforting myself.

But the only entertainment I have was coal and water.

however?

The newbie took everything and ended up being dragged to the slaughterhouse.

"That bitch. At least give me back the coal."

"Damn, I thought I wouldn't be bored for a while since there's a newbie."

The atmosphere in the repentance hall had become tense.

They say that when people have no trouble making a living, the emotion that was most difficult to endure was boredom.

But no matter how bored I am, there was nothing to do.

So I just lie there and do nothing, and time just seems so slow that it doesn't seem to pass at all.

The penitentiary was a way for prisoners to slowly rot away.

That was when.

"Ta-da! This girl is back!"

A cheerful voice echoes throughout the chapel.

The prisoners in Repentance Hall were ridiculous.

Now that he didn't even have a Kunlun horse to accompany him, he just walked in on his own and stood firm in the hallway.

"No, you bitch, how did you come back alive?"

"Who am I? The King of Apparatus. There is no door in the world this Cha Xiantian the Annihilator of Doors cannot open. Even if they were enemies, I am the owner of words that open wide the doors of their hearts and gain their forgiveness. Ah, am I the strongest in words? Truly, being great is a sin, a sin. I am the sinful Supreme Being."

It was a sound that left the speechless.

Then, Dumpling Earss, who were petty and did not hide his hostility, sneered.

"Aren't you saying that you ended up apologizing profusely and saying you were wrong?"

"Huh. You idiot. Who's even my enemy? Do you think Cha Xiantian the Annihilator is called the Annihilator for nothing? Unlike you, I don't leave any buds that could become enemies like a retard. Especially you, Dumpling Ears. What? Killing them quietly because it could cause trouble later? That's why you're here like a retard. Because the idiot was so clumsy that he can't even clean up after himself."

"I'm going to rip this bitch's mouth off-"

"Really? Here, tear it. Tear it. Yeah. Like your testicles that were torn. Oh, right. Since I'm out here, I should've looked for pig testicles. It's empty and frivolous, like a woman's, and it makes you feel a little more substantial. If you put it on the bottom, it'll make you look more substantial."

"You, you, you bitch……!"

"Oh, don't use such strong language. It makes you look weak."

\textit{The Dumpling Ears were turning bright red. Hmm, what was this? Is it a spicy chicken dumpling? Hmm, I want to eat spicy chicken.}

\textit{If I boil the noodles and simmer them in spicy chicken broth, will it taste similar?}

\textit{I'll have to try it when I get back to the Divine Maiden Sect.}

\textit{Since women originally like spicy food, I think everyone will like it, but what if they like it too much?}

\textit{Isn't it like making a dish named after me, like Dongpa Pork?}

\textit{Hmm, Qingmyeon? Since it's spicy noodles, Qingmyeon?}

In any case, the prisoners of the Repentance Hall who were listening thought that at least one fact was worth acknowledging.

They say she's the best at speaking, and her tongue-twisting skills were certainly extraordinary.

Well, the seal has now been released.

I realized the true meaning of repentance.

So, can't I just tease him?

"Whether it's annihilation or whatever, isn't it still the same thing that the enemy came looking for you?"

"Kukuku …"

"What? You're saying they weren't enemies? Then?"

In the next room, the poisoner, who speaks in a somewhat noble tone, shows a satisfied reaction.

"Hmph, that's the difference between you and me. A true friend comes to your aid in times of need. I have many true friends, and all you had were just a bunch of idiots who clung to you and flattered you. It's obvious even without looking. They were just followed you around calling you 'brother', right?"

Qing started saying whatever came to mind.

"Look at you guys right now. When things were going well, you were like big brothers and big shots, they were sucking up to you like you were nothing but kings. But look at you now. For at least ten years, or at most thirty-five years, not a single person has come to save you. My goodness, you've lived your life so frugally. Tsk tsk."

"Ahem."

The prisoners coughed uncomfortably.

Then again, wouldn't Dumpling Ears be the one to make a fuss?

"You retard, you're so excited to be making such a fuss. Do you think I'd just sit back and watch since I'm not retard?"

"Why? You want me to swear at you like some little sissy? Yeah, go ahead. Who would listens to such nonsense? 'The bastard you just mentioned as her enemy was actually part of the gang trying to help her escape!' Wow, that's so surprising!"

Qing continued to taunt with a chuckle.

The face of the mandu ear was now flushed red as if it had been painted with red wine.

"Come on. Pay attention. My friends say, 'Is it possible to take another one?'"

The prisoners' eyes suddenly changed at that.

Half doubt, half hope.

Even if you're not necessarily a positive thinker, this was a huge change that would surprise and awe you, saying it was half hopeful.

Because for a moment, light flashed in his dull eyes, like a rotten fish, just listlessly.

Wow, look at these bastards' eyes.

Of all faith, hope, and love, isn't hope the greatest?

Even in the box of disaster opened by Mrs. Pan\footnote{Pandora}, the thing sealed deepest inside was hope.

This was because hope was the cruelest thing, the most cruel and dangerous blade in the world.

So that was the weapon that Qing took out.

"Ah. Of course. If things get tangled up along the way, I'll just abandon you. Yeah, to be honest, I'll just use you as a bait. I could use you to buy time. But hey, if things work out, you could escape happily, right?"

The suspicion in the prisoners' eyes was greatly reduced.

Because the idea that they could be used as a bait seemed even more believable.

"Okay, I'll pick one. Of course, if there's a going, there has to be a returning. What can you give me in exchange for your freedom?"

A sinister smile spread across Qing's lips.

White teeth, with particularly sharp canines were on full display.

"By the way, I don't accept postpaid payments. You understand?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Lundokinjin. This old monk was the chief priest of the Blood Rain Temple, pronounced Lunduprinjing, the brightness that exists on its own, according to the chief priest.

But contrary to my name, I've been feeling quite weak lately and haven't even been able to properly care for my hair.

So even his bald head grew a bluish color and lost its luster.

You could even say that it's not worth the name.

No matter how bright the light is, if it harbors great worries within, how can it be splendid without shadows?

Lunlin couldn't stay still and wandered around aimlessly.

The pursuit party that set out to capture the traitor to the nation never returned.

Even though he lost an arm, he was still a monster, and he was as vicious as he was eccentric, so he sent two of the best martial artists to follow him.

If it's just taking time because the guy isn't caught, then it wouldn't matter, but what if that's not the case?

What if you were captured by the Kunlun Malkos?

If that's the case, those bastards with a pretext, Zhongyuan' lackeys who oppress the Western people and enslave them, might invade when the time comes.

However, the elite of the Blood Thunder Demon Masters, the Vajra Monks, show no sign of returning, let alone sending a single letter.

Even if he was the Blood Thunder Demon, there was no guarantee that he will win against the Kunlun Sect if he was the only master.

It won't collapse easily, though, as the headquarters has built up its defenses over many years.

But what if they drag the government into it?

What use were the fortified headquarters facilities and the formations and traps in front of the cannons?

So, Lunrin couldn't help but feel anxious and worried, thinking that all the training she had put in so far was in vain.

"[Should we withdraw headquarters now? But, leaving behind our compatriots in Qinghae, our Bloody Thunder Company, symbolizing the spirit of the West Commander, cannot withdraw. Ugh, what can we do?]"

Then he stood with his palms against the wall, turned around, looked out the window, and sighed.

My shoulders were stiff, so I moved awkwardly, clenching and unclenching my fists for no reason, and then I started chanting while rolling my prayer beads.

"[When on earth will Podalap's reinforcements arrive? The Great Master has promised that he will spare no effort in providing support for the uprising.]"

In fact, that was the reason why I didn't pack up and retreat even though something seemed wrong.

Because the reinforcements that Podalap promised to send to help recover Qinghae were promised to be headed by Emperor Geotap, the supreme warrior and the foremost general of the West.

Originally, in Buddhism, the term Cheonwang refers to the guardian who protects Mount Sumeru, the center of the universe where the main Buddha resides.

The common term, the Four Heavenly Kings, originates from here. The four heavenly kings, Jiguk, Gwangmok, Jeungjang, and Damun, who guard the east, west, south, and north of Mount Sumeru, were called the Four Heavenly Kings, the Four Heavenly Kings.

So, how lofty was the name of the Giant Pagoda Emperor?

When we say a tower, we mean a Buddhist tower, and we mean the Buddhist law itself.

But it was not just a tower, it was a great tower, it was a great wisdom, a great Dharma among the Dharmas.

Not the Heavenly King, but the Emperor, a true guardian higher than that.

So, isn't the Emperor of the Giant Pagoda a rank that can truly be called the incarnation of the main Buddha?

I heard that the first person in the West has already reached a state of profound wisdom.

That was when.

"[Master, a guest has arrived from the west gate, and he says he has been sent by the great master.]"

Come! You're finally here!

Runjing's expression brightens as if all the worries he had been having until now were washed away.

Of course, it was a frivolous smile that did not suit a Buddhist.

The smile of Buddha was the most subtle and mysterious, subtle and subtle, so it does not make the face that was bright like a child look big.

Finally, the Emperor of the Tower, the first person of the West, appears as the head priest.

If you're so skinny, wouldn't something like a mountain skeleton walk in?

"Oh, the Emperor has arrived! Indeed, the Master looks truly orphaned!"

This was because lamas consider it a virtue to be thin and have visible bones.

The chief priest said that religion, government, and martial arts were all one, and since he was a monk, government official, and military man, wouldn't the power of the lamas be infinite and endless?

So, if you eat well, rest well, and play well, you will end up gaining weight.

So, the culture of the chief, who was praised as he dries up, was the minimum safety device to keep away from the luxury that comes from such power.

But compared to that, Lun Lin's appearance was quite stately and had a lot of flesh on it.

How come?

Since the Blood Thunder Shrine was in Zhongyuan, did it follow the custom of the Zhongyuan?

How could that be?

Virtue was inherently difficult to maintain.

Even if we consider flesh on a skull to be the highest virtue, in reality, there were not many people like that.

That was why, on the contrary, thin people could be praised for their high virtue.

If Qing had known, she would have been able to tell at a glance that although Amukhaprap was a strange man, he was a decent monk in his own right.

Qing still didn't know much about Zhongyuan culture.

To demand that Qing embraced the culture of Xizang was too harsh.

You shouldn't even expect it.
