\chapter{The Showdown Between the Kunlun Sect and the Blood Thunder Shrine (12)}

Qing was a little worried.

What if you could teach me the Emperor's Sword? Should I just pretend to be clumsy?

Of course, I know that's not possible.

But still, you never know.

But asking you to teach me something and then ask me to do something wasn't like asking me to come up with my vision, like a robber.

"Okay, just a little more. I need to figure out the internal structure first, right? Oh, the Shingeom Unification was going to be solved. Hmm, surprisingly, this part was a bit frustrating. I thought I'd just learn it after being shown it a few times."

It was literally talking about the various scraps that come out during the process of a master of martial arts, a master of the present world, studying martial arts.

The iron club in Qing's hand trembles.

It was shaped like an iron sword, but it was a roughly made skewer with no blade or shape, so it would be more accurate to say it was an iron club.

Qing was sweating profusely and her hands were shaking.

"This isn't easy."

"That wouldn't be easy. But once you get the hang of it, there's no better lifesaver."

"Hmm."

Since Qing was a man who learned martial arts raw, it was not easy to grasp the tricks of even a simple technique.

Well, from the perspective of Qing, the techniques used by the masters of Hyeon-gyeong were very high-level techniques.

The act of recklessly pushing energy into the sword while maintaining the unity of the divine sword, and continuously compressing and building it up inward.

It sounds easy when I say it this way, right?

The amount of force needed to push the sword in without breaking it must be enormous.

As the old joke goes, it was like putting an elephant in the refrigerator.

"Hmm. Why can't you do it? Just hold the sword well, maintain the unity of the mind and the sword, and feel the structure. Then, spread the energy inside the blade. It's not about putting it in, it's about manifesting it."

It was easy to explain as Nan-Gong Daero, but it feels easy only when you were at the right level.

One. Open the door.

Two. Put the elephant in.

Three. Close the door.

Well, this was the level of solution.

Miss, does this make sense?

It was a moment when I was slowly getting annoyed.

"Oh, that was a good feeling just now! Yeah, that's the feeling. If I remember it well and spread it around little by little, well, it'll work out, huh?"

How does it feel?

Is this a good structure to work with if you get annoyed?

Qing applies brute force to the handle, straining his eyes as well.

It seems like something was going to happen?

But what on earth does being annoyed have to do with being compressed?

But I do it because I can.

Well, you don't need to know the principles to do something.

When I say I'm annoyed, I think of that bad girl's half-and-half face and shameless expression, and it seems like I'm feeling even more annoyed.

In fact, it was not annoyance but the ability of the Gwangyochusalganggi to react to the desire to live, but neither Qing nor the Sword King knew.

Nan-Gong-daero had an ambiguous expression.

I thought you could just follow along roughly, but it turns out you're actually following along step by step.

It's disappointing for a Cheonhwageom, but considering it's the early days of Hwagyeong, it's quite an amazing achievement.

It was a technique called the Infinite Wave Sword.

Endless Sky, just hearing the name makes you think it's Nan-Gong-like, but what can you do since it was actually created by the Nan-Gong family?

It's not quite a herbivore, just a move.

However, the power that the Sword King showed was not just a single move, so Qing rushed to learn it.

"Hmm. I guess I can practice on my own at this point. Since we're leaving soon, I thought I'd check on Kunlun. Is that okay?"

"Of course. Thank you for letting me know."

Nan-Gong Daero smiles happily at him.

How can my son do well?

No matter how much I think about it, that kid won't do anything good, but still, you never know what will happen between a man and a woman.

Of course, it doesn't have to be Cheonhwageom, but the Sword King wanted to bring in any woman he could.

So the three police officers prepare to go on a mission.

The time to set out for the Blood Thunder Temple was approaching.

Meanwhile, Qing was holding the sword and trembling.

It's frustrating when something seems like it will work but doesn't.

Yes, another day, another day, another day, another day, with the determination to see who would win, I devoted myself to practicing the Infinite Sword.

A few days later like that.

A loud noise, like a bomb exploding, shook the mountain temple as the Kunlun sect went on a final inspection before departure.

Nan-Gong Daero smiles happily at him.

The three masters of the three realms revealed their identities just before the battle, and a thunderous roar erupted, piercing the heavens.

Of course, the best in the world, the best in women's middle school, and the king of swordsmanship were all gathered in one place, so it was only natural that the disciples' morale was high.

Even with two swordsmen who were the best in the world and respected, how could I possibly tolerate it?

Because I couldn't reveal my identity before that.

Because my disciples, who were so excited by seeing their idols, would never be able to control their mouths, they would just blurt out, "Wow! What a sight!"

Even if just one word gets through to Xinying, it takes more than a day for the news to spread in the quiet winter.

The operation became a bit strange with the addition of the three Hyeon-gyeongs.

Before that, the atmosphere was solemn and solemn, with people swallowing their saliva in nervous anticipation of a real match.

That's true.

Hyunkyung, three?

Is there only one flower garden there?

Can't we just watch?

It's only natural that a life-or-death struggle suddenly turns into a picnic.

like this.

Kunlun Sect begins its advance with Blood Thunder Temple.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Simaanggeum, Siang was a common female name in the West, pronounced by the West, Nimayangjun, Niyang, meaning a woman born in the hot season.

I used to hate this name, which was so unrelated to the castle, but not anymore.

From the moment the lowly chief's wife died under that hot summer sun and opened her eyes to something new.

I started to like this name, thinking, "Isn't it a truly fateful name?"

Siang lifted the silk cloth that was hanging down from under the bed and stuck his head out as he spoke.

"[Your Majesty? I heard the Kunlun sect has departed?]"

Then, looking at Siang's face, Emperor Geotap, who had a frown as if he had seen traces of someone vomiting, suddenly stood up without answering.

And then, without even looking back, wouldn't he just slam the door and leave?

But Siang was smiling brightly.

"[Oh, you left without even listening to what I said. I heard there was someone who looked like the Sword King. Hehe. Well, I guess you wouldn't have told me anyway.]"

Because there must be a Cheonhwageom there.

Of course, Unyeonyeong never once asked for consideration for Cheonhwageom's circumstances or anything like that.

But everyone knows.

Wasn't Cheonhwageom the special person of Unnie?

But how can we be so cruel?

Siang chuckles and thinks of his beloved Creator.

"Oh, I didn't bring you back to life hoping for something, did I? I just failed at making friends. So, you can live however you want. Then, have a happy second life."

It was an answer to the question of what must be paid in exchange for a new life.

But most of the Zaring Jiangshi wanted to help their beloved creator, and so did Xiang.

Of course, there were some sisters who consider themselves monsters and leave.

Why the hell were we monsters?

I can't understand.

Regardless of the understanding, the Jaryeong Gangshi were still on good terms.

Well, that's because that's the kind of being he is.

Life was infinite and nothing was needed to survive.

There was no reason to hate each other just because we have different opinions.

Because I am no longer human.

There was no reason for them to fight, steal, and hate each other like humans do.

but.

We were failures.

But I have no regrets about it.

I just couldn't become a greater being.

Because the moment I opened my eyes again, I realized that I had already become a being superior to humans.

But the Cheonhwa Sword was not like that.

One who can be the Creator's true friend and understander.

A foolproof method to resolve the loneliness of the great being we cannot resolve.

"[Hey. I heard Cheonhwageom was so beautiful. I should go see her face.]"

Siang quickly slips out from under the bed.

The Emperor of the Tower told me not to let a single hair stand on end, but he had no authority to give orders to me in the first place, so it was entirely up to me whether I would listen or not.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"[I looked in with my supernatural powers and saw that the Kunlun Sect bastards were starting to gather. I will now unfold my formation, so all disciples of the Blood Thunder Sect should vacate the headquarters.]"

It was the Giant Pagoda Emperor who talked about supernatural powers without even licking his lips.

"[at las!]"

Runlin clenches his fist and lets out a gasp.

The great emperor possessed many wisdoms to annihilate the invaders of Zhongyuan.

One of them was Jinbeop.

That too, the terrifying Manra Daehyeolmyeolcheonjin!

Actually, Runlin doesn't know what it is.

But isn't the name scary?

I heard that it was a terrible formation that kills everyone, including the person who deploys it, as there was no way out of it.

They're just trash that's messing up the grounds anyway.

If you die with the Kunlun horse while unfolding the formation, you should rather die grateful for the opportunity to practice virtue.

But if a person from Zhongyuan heard about it, it would be a horrific method that would shock them.

It was a blood sect's most precious sacrifice, requiring at least three thousand human lives as offerings, and even then, only three thousand lives could be used with utmost care, without wasting anything, such as the brain, eyes, and heart.

But the blood relationship did.

Because, since we're going to burn three thousand non-blood sect members anyway, wouldn't it be a huge gain if we could just kill one enemy?

Besides, there were only about three thousand people in Zhongyuan.

The Giant Pagoda Emperor was now licking his lips.

I will dismantle and kill each and every one of those who were caught up in the chaos.

Since he was planning to kill everyone, isn't he also trying to kill himself?

Of course not.

The method doesn't work on true masters.

When you reach the level of Hyeon-gyeong, you will gain the ability to see through even the distorted nature of the truth.

So, for Emperor Geotap, once the formation was spread out, it becomes nothing more than a comfortable playground.

I think it was called a thousand-year-old girl.

How happy would the Jeongpa bastards be if they turned the Kunlun sect's leader into a blood demon and sent him back!

Even without that, the business was failing one after another.

Once he has accomplished this, wouldn't the Hoeju also realize the excellence of the Xijang people and treat them with respect in the new era?

Anyway.

The glorious future of the Xijang people was drawn in the mind of Emperor Geotap.

One person of the Western race will have twenty Han Chinese slaves.

Since all Han Chinese were slaves anyway, their numbers will be overflowing.

All Han Chinese women must conceive a child of the Western Zhuang people as their first child, so that the Western Zhuang people will fill Zhongyuan.

For reference, this was a system that was actually practiced in the Yuan Dynasty, and it matches perfectly if you replace Mongols with Xiamen.

Just a little bit of a blank expression.

"[Your Majesty?]"

"[Ahem. In case you get caught up, retreat to the southern ridge.]"

"So, when can I step down?"

The Emperor of the Tower frowns as if asking what he was talking about.

"What were you talking about? You're not going right now."

"[Huh? Are you saying this so suddenly? Are you planning to deploy it immediately, rather than when the enemy comes close?]"

Of course, at the Blood Thunder Temple, people's long-term strengths and the mysteries of the human body will be on display.

I can't show you that kind of appearance, can I?

"If an outsider makes a mistake during the preparations, everything will go down the drain. Don't even think about lurking around; just stay away."

"[Are you saying that we can't even come to get food?]"

"[What did you hear from me?]"

Runlin was in a difficult position.

Don't even approach me.

Even if you bring plenty of food.

Even if Kunlun arrives quickly, it will take at least ten days. How will I get through the night during that time?

But even if that were the case, what would happen?

"I will follow your words."

If you feel wronged, you should have become the emperor.