\chapter{Let's Have a Spar (7)}

To be fair, Tian Youxue had a plan.

The Blade-Life Training Method was a secret technique passed down through ancient traditions of close-quarters martial arts. Its true purpose was to heighten the senses to their absolute peak.

That it made her movements softer—well, that was more of a side effect. Or maybe an unexpected bonus? Either way, it was never the point.

A blade could never fully replace a person's hands. So, to overcome that, one needed hypersensitive perception, incredibly fine motor control, and perfect balance.

That's why, when Qing inevitably failed and started questioning if this made any damn sense, he was going to step in with a flashy demonstration and recommend a particular technique.

It was called Flowing Flex Technique—an external-body cultivation art, as its name suggested, meant to temper the body into a fluid and supple state.

Unlike internal cultivation arts that focused on building inner energy, external cultivation trained the physical body itself. A famous example would be Shaolin's Diamond Invincible Body Art.

"Well, uh, yeah. I mean, that much is expected. Still… you've got a bit of talent after all."

"Oh? Really? I have talent?"

Qing lit up and asked again.

It was actually the first time she'd ever been told she had talent without the help of her status window.

Ever since yesterday's dinner—cutting up her clothes in the middle of the night, then battling breakfast this morning—she'd spent eight full hours grinding without rest. Maybe her effort was finally paying off.

She was feeling kind of proud of herself.

Still, if her status window had feelings, it'd be screaming right now.

All she'd really done was brute-force mimicry, thanks to her monstrous base stats. It wasn't like she had unlocked some clever trick—she was just overpowering it with freakish body specs.

It was kind of like running.

A naturally talented runner would quickly figure out optimal posture and breathing and improve fast.

But in Qing's case? She was just mashing the ground into submission with pure leg strength.

Still, if her record looked the same, people watching couldn't help but assume she had talent.

"Even so, you're not there yet. Whether you're using bare hands or a dagger, it should take the same amount of time, right? How long did dinner take yesterday? What about dressing?"

"Uh. Well, yeah. But won't I get better fast?"

"After that, you'll have to do it with your left hand. And eventually, you'll need to live your daily life with two daggers in both hands. Only then can you say you've grasped the true essence of the Blade-Life Training."

"Ah…"

And then Qing suddenly asked—

"But… do I really need to master the ultimate essence? I just need to get the feel of ‘softness,' right?"

"Ahem. But if you do reach the essence of the Blade-Life Training… wouldn't you naturally unlock the essence of softness too?"

"Hmm. Do I really need to go that far…"

Tian Youxue flinched. He tried to soothe her.

"Is it too hard? Actually, there's a complementary technique that's normally practiced alongside Blade-Life Training. You'd progress much faster if you train both together."

"Ooh, there's a technique like that?"

"Of course. It's called the Flowing Flex Technique. Huh? Where are you looking? Is something over there?"

"Ah. Just thought I saw something."

Qing quickly pretended to be distracted.

But Tian Youxue wasn't the type to miss even a flicker of a glance. That was just how he was.

\textit{Flowing Flex Technique. External-body art. Gold rank.}

\textit{Sure, it was technically a supreme technique… but gold rank? Really?}

\textit{Does this guy even have a purple-rank art?}

\textit{What a joke.}

If Tian Youxue ever found out, he'd have gone absolutely ballistic.

'This is a supreme art too, damn it! A world that only respects top-tier techniques is corrupt to its core!'

"So, will you be teaching me the Flowing Flex Technique too?"

"Of course. One formal student's bow and—"

"Sorry, no."

"…You cut me off cold. Just like that. At least think it over—"

"Still no. Sorry."

"Goddammit! This is a Divine Art too, you know! Look! You're a swordswoman—you should be able to see how incredible this is!"

And then Tian Youxue started twisting his wrist this way and that. It was so absurdly flexible it looked grotesque. When he bent it backwards, the back of his hand nearly touched his forearm. When he bent it forward, his palm almost hit the other side of his wrist.

It bent over ninety degrees sideways too—his joints had a range of motion that was straight-up inhuman.

Then he extended his arm and hyperextended the elbow so far it looked like it bent the wrong way. He swung it in a huge circle, and the arc was so perfect, it didn't veer off at all—just a perfect straight line.

For any martial artist, swordsman or not, that kind of flexibility would be enough to make your eyes pop out.

If your joints moved like that, the range of motion for your techniques would expand a thousandfold.

But honestly, Qing was below-average when it came to applying this kind of thing. She only used what she had—she didn't know much about how to adapt.

"Oh wow. A circus act. Last time you were selling books—do you sell potions too?"

"Circus act?! Are you calling me some dirt-cheap snake oil vendor?! You really don't see the value in this? I'm offering to teach you this terrifyingly powerful art for free!"

"Hmm. Even if I wanted it, I can't serve two masters. It's a shame, but I'll have to pass it on to someone else."

"Unbelievable! You're as thick-headed as a brick wall! How is someone this hopeless even real?!"
	
Tian Youxue pounded his chest in agony.

Qing thought, \textit{He's gonna bruise himself at this rate. He was hitting so hard it looked like self-harm.}

"Look, you've got all these incredible techniques. I'm sure you can find a student other than me, right?"

"Hmph! Maybe if I hadn't met you! But once you see the world's rarest gem, who the hell settles for anything else?!"

"Hehe… I'm not that great…"

Qing scratched the back of her head, bashful.

Watching that, Tian Youxue's insides just exploded.

And yet, he only became more obsessed.

At first, he'd just thought she had a good eye for rare manuals.

Then, he figured she was incredibly fast.

But after putting her through Blade-Life Training, he realized she had all the needed talent for a Divine Thief.

And look at that loyalty.

If she was that devoted to her current master, she'd be just as loyal to him if she became his disciple.

How could he not be greedy?

Even if he found someone else, he already knew—he'd think of her constantly and regret it forever.

"Hmph. Just you wait."

"You really don't have to. Well then—"

Qing gave him a small bow and backed away.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Henan cuisine was known for combining the characteristics of all four directions—east, west, south, and north.

In other words, you could say it was a jumbled fusion dish with no distinctive identity unique to Henan itself.

Still, if one had to define its culinary tendencies, rice was the main grain, but they rarely ate plain white rice—instead, it was always fried rice. The noodles were also mostly rice noodles.

And most importantly, no region in Zhongyuan loved onions more.

Which made it incredibly inconvenient to eat with a knife.

Fried rice, to be considered top-tier, needed to have every grain separated and loose. And the onions? Sliced into thin strands.

Qing carefully stacked a heap of fried rice onto her dagger and lifted it over her head. Unsurprisingly, a rain of rice grains came showering down onto the table.

Then she tilted her head back, stuck out her tongue, and tried to dump the food into her mouth—four bits dropped onto the table, three splattered against her face, and only three actually made it inside.

Honestly, Peng Daesan had only made a single comment when this all started, and then stayed quiet.

Not because he respected her 'dedicated training', but more because watching a stunningly beautiful woman make a complete fool of herself was weirdly entertaining.

But seeing Nan-gong Shencai doing the same thing? That was a bridge too far.

"What the hell are you doing at the dinner table? Brother Nan-gong, seriously, why are you joining in?"

Peng Daesan groaned.

Nan-gong Shencai was outright struggling to eat with a longsword in hand, the blade crossing over the table in a way that could only be described as irritating.

"Hm. I saw Sword Friend doing it, and this training seems to have real effects. Didn't you experience it yourself today?"

"There's no guarantee that was because of this training— Wait, no. Sister. Why are you holding a blade? I… I refuse to believe you're doing this too."

"I was thinking… I've been so lazy. I go around calling myself a disciple of the Blade, saying I'm married to my saber—how shameful. Watching Qing'er made me realize it. Every moment of breath should be part of one's training."

Peng Daesan's face twisted into a grimace.

Now that he thought about it, Peng Chaolei was also famously unhinged.

It was just that people treated her like a big sister because she was the Jade Qilin's sibling—but deep down, she was a training-crazed blade addict just like everyone else here.

"…What the hell am I looking at."

Peng Daesan let out a long sigh and reached out with the large tongs to grab a hefty chunk of braised pork belly.

"Yap!"

Suddenly, with a cute shout, a throwing blade came flying in and skewered the pork belly.

Then, trailing along the thread tied to it, the chunk of meat soared through the air and landed neatly on Tang Lan-Ah's personal plate.

"See? That's why you gotta choose your weapons well. Look at that. How convenient."

She was holding a long acupuncture needle—basically a skinny chopstick.

Peng Daesan stared at Tang Lan-Ah and thought, \textit{She's getting more annoying by the day.}

Wait, no—wasn't she already like this when they met?

Peng Daesan was confused for a moment.

Now that he thought about it, the very first time she opened her mouth, she said something like 'official wife' or whatever. 

She'd been an annoying little gremlin from day one. So maybe she was just consistently annoying.

Peng Daesan sighed and reached out with the tongs again.

"Yap!"

Another throwing blade. Thunk.

"…What are you doing now?"

"For Qing'er. Qing'er, here, eat this. Training's great and all, but you still gotta eat. Come on, open up."

She twirled the thread like a pro and flung the meat chunk right onto Qing's plate.

"…I'm going insane."

Peng Daesan dragged his hand down his face.

And speaking of people going insane, there was one more.

Qing.

Qing loved to stuff her cheeks full, to the point her face looked ready to explode.

But with nothing but fried rice crumbs she was awkwardly poking in with her dagger, it was starting to drive her up the wall.

Eventually, she snapped and reached for a Shaobing with her knife.

Shaobing, one of Henan's signature foods, was a flatbread baked against the walls of a clay oven.

Qing stabbed the underside of the bread and gently lifted it, then took a big bite.

She smacked her lips and began slowly pushing the crispy bread into her mouth—but Shaobing, famous for its crusty outer layer, wasn't exactly cooperating.

The disaster that followed was entirely due to a lifelong bad habit.

As the bread began tearing along the bite marks, Qing instinctively moved to push it into her mouth with her hand—

The problem was, her hand was holding a dagger.

So she accidentally angled it point-first and jammed it straight in.

The legendary dagger—famous across the martial world for its sharpness—sliced straight through the Shaobing without resistance and—

CLANG! The dagger dropped to the floor.

"AH!"

A scream, rich with panic and pain.

Instantly, the guy struggling with his sword, the girl grappling with her saber, and the rest of the martial lunatics all turned their eyes toward Qing.

She had a hand over her mouth, blood pouring down from underneath.

Not trickling. Pouring.

"Qing'er! What—what happened?!"

"Huuh… huer… hul poked."

She meant she stabbed her tongue.

And by the looks of that bleeding, she really stabbed it.

But Qing had her eyes lowered, her face full of shame. The embarrassment must have outweighed the pain.

Realizing it wasn't a serious injury, Peng Daesan finally let himself exhale and groaned out a deep, long sigh.

\textit{Yeah. I knew this would happen.}