\chapter{Let's have a Feiwu (1)}

To be honest, Qing had just apologized with the intention of letting it go.

After Murong Zhuji's grand explosion in the drinking contest, she didn't particularly hold any grudges.

Still, it was tiring to growl every time they met, and for Jun's sake too, it seemed good to resolve things at this point.

Moreover, even though Murong Zhuji had been firing off insults left and right, everyone just sighed and let it slide, which made it even more so.

The rising stars who kept rubbing against each other just glared with hateful eyes, but that was all, their cute revenge was just 'Just wait, I'll completely humiliate you'.

However, Murong Zhuji's automatic sarcasm was an extremely dangerous habit.

If she accidentally offended even a witch from the Unorthodox Path, she could lose her head without being able to say anything.

So well, if her habit could be corrected now, it might save someone's life later.

Anyway, Qing achieved her purpose in attending the Dragon-Phoenix Assembly.

She had decided to stay at the Wucheon Pavilion from now on, alternating between training and rest to refine herself, so wasn't this the last Dragon-Phoenix Assembly she attended to announce 'Those who want to join me, gather here'?

To return to being Ximen Qing, the prepared talent and martial artist, from the lazy Ximen Qing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After the sparring match that ended in just a few exchanges, Nan-gong Shencai said with a serious expression.

Because Nan-gong Shencai is always serious.

"I felt this last time too, but Sword Friend's skills have become even more meager. It seems you've relied too much on strength. Hmm. Since martial arts were originally created for humans to surpass their limits."

"What does that mean?"

"Sword Friend, hasn't strength become your strong point? So you just swing with force, but in terms of skill, haven't you rather regressed?"

There was nothing to say even with a hundred mouths, because Qing's fighting had always relied on strength and tricks.

Creating openings with brute force and even more monstrous inner power, using Buddha's Palm and Divine Maiden's Hand, using poison if there was poison, and occasionally using demonic arts when appropriate.

For reference, the Divine Maiden's Hand is a state where divine arts and demonic arts overlap, so since it's divine arts when our side sees it, it can be used openly with dignity.

As a result, the movements she uses tend to be simple, large, and powerful.

Nan-gong Shencai revealed the peony sword that had disappeared above the handle, showing its pointed cross-section.

"In a duel to the death, I would have no way to defeat Sword Friend. But in sparring it's different, because we're just comparing skills and have to be considerate not to hurt the opponent."

"Hmm. As expected of Sword Friend. This is the kind of diagnosis I wanted to hear. What should I do?"

"You don't need to be too fixated on winning or losing. It's not a duel to the death. You should think of it as experiencing unfamiliar skills and dealing with them, not trying to decide a winner."

Qing obediently accepted the advice.

This is what having good friends is all about.

"Alright. Come, Sword Friend! The Wooden Light Sword is hungry!"

"Good! I'm coming!"

And so, Qing vs Nan-gong Shencai. One win, nine losses.

Qing was frustrated by the unbelievable result.

Even the one win could be considered invalid because it was the result of overpowering with strength.

"What's this, why do I keep losing? Surely humans weren't designed to lose. Sorcery, it must be sorcery! You, Nan-gong Shencai, what kind of sorcery did you use!"

"Well, sparring isn't such a fair competition to begin with."

Sparring isn't originally done to decide a winner.

Still, if we were to compare advantages and disadvantages, martial arts that focus on subduing rather than killing are much more advantageous, and martial arts based on softness rather than strength, on technique rather than simplicity, are much more advantageous.

And Qing liked to strike down with strength that transcended humanity, with the killing star containing heavenly slaughter.

It was absolutely useless for sparring.

"This is a completely tilted sparring arena, isn't it? What kind of match is it without chariots, cannons, and even horses?"

"We can't have a duel to the death either. Besides, it's not much different from the martial arts competition, so why don't you think of it as practice?"

Even if Qing complained, the Hidden Dragon Martial Arts Competition wouldn't change to ‘Duel to the Death \sout{Everyone's Survival Competition}‘ or anything like that.

"Well, if push comes to shove, I can just use strength…"

As a special rule for training sparring, if either of their wooden swords broke, it was Qing's loss. That's why the dismal record of one win and nine losses was inevitable.

It was a special measure to reduce Qing's reliance on strength and train her skills.

"Sword Friend, it's not good to leave such an escape route. You should think of it as competing with skill."

"Originally, if there's no escape route, you shouldn't enter in the first place, right?"

"Hahah, I can't beat Sword Friend with words. Come, let's go again!"

And so, another five rounds, one win four losses.

She recorded twice the win rate, should we call it rapid progress?

As Nan-gong Shencai stepped back to catch his breath, Qing gestured to Peng Daesan this time.

"Now, next is San. Come on in."

"You want to spar right now? Without resting?"

"I feel like my body is just nicely warmed up? Now that I'm getting into it, I shouldn't miss the timing."

"Hmm. Your stamina is good. Don't think about making excuses after losing."

"Oh. Are you provoking me? Are you going to talk with your mouth instead of using that good half-sword?"

"That damn half-sword…!"

And after Qing won twice in a row, she lost eight times in a row.

It was because of Peng Daesan's vile tactics.

"How can you just aim for the weapon! You're completely determined to win!"

"Isn't a rule a rule? We said it's your loss if the weapon breaks."

"It's just sparring, are you going to be fixated on winning or losing?"

"It's no use saying that after winning and saying all sorts of things."

Qing frowned.

She had just won twice in a row and said a few words, but the man got sulky and cowardly.

Peng Daesan just induced clashes with strong attacks and pressed on, so if she responded with strong attacks, the wooden sword would break right away.

Moreover, the wooden swords were so weak.

After the ebony wooden sword broke in the last Dragon-Phoenix Assembly sparring, Nan-gong Shencai diagnosed Qing's condition and ordered special cheap wooden swords made of softer wood.

It was Nan-gong Shencai's warm-hearted gesture for Sword Friend's growth.

One crate in the carriage, and when the consumption rate became alarming, two more crates arrived later, making it a somewhat heavy-hearted gesture.

He prepared that much not knowing when they'd be used.

"Sword Friend, should I pay for the wooden swords? I'm using them all up…"

"Even if you paid for all of them, it wouldn't be half the price of the ebony wooden sword Sword Friend broke last time. They're all just roughly shaped from firewood that's only good for burning. Isn't it interesting that the center of gravity is all different?"

"Hmm."

"Besides, what's a bit of money in the seat of sword judgment where we share swords with Sword Friend."

"Sword Friend! I'm moved! No, sword-moved! Sword-grateful!"

"I like sword-grateful! I too am sword-grateful! Come! Let's share sword judgment again!"

At this, Peng Daesan's eyes narrowed.

These guys are really playing around, he thought.

"Sword Friend, take a break. San! Come here!"

"San, catch your breath a bit. Sword Friend! It's your turn."

And then Qing alternated between the two.

Focusing on breaking perfectly good wooden swords one after another, broken wooden swords piled up in the Wucheon Pavilion training ground.

It was a sight that made it look like she had a grudge against wooden swords.

As a whole pile of what used to be wooden swords accumulated into a heap of firewood, the sun had set and darkness had fallen.

"Huff, hah, next, San, hah, whew…"

Qing called out, soaking wet.

It was natural since she had been swinging for two and a half shichen straight without resting once.

At this, Peng Daesan and Nan-gong Shencai exchanged glances.

'Brother Nan-gong, it's a bit strange, isn't it?'

'Yeah. More than training, it seems like she's desperate to overwork her body.'

After exchanging opinions like this, the two men subtly changed the topic.

"Sparring is good, but aren't you getting hungry?"

"Yes, Sword Friend. Training is good, but you must also take proper meals."

The effect of the customized topic change was tremendous!

Qing opened her eyes wide, then immediately licked her lips.

"Oh? Wow, I forgot about eating? I'm completely starving. Let's eat, let's eat."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Guangzhou in May is already in the midst of weather that could be called hot.

At least it's cool at night, so inns, restaurants, vegetable shops, tea houses, and all sorts of places set up temporary tables on the roadside to receive customers.

Under the warm lighting of lanterns hung on ropes between buildings, an old woman and a young woman were having a meal.

They looked like an old woman who had brought out her sickly granddaughter, and even to an animal's eyes they must have looked easy prey, as a stray dog was sneaking closer, watching for an opportunity.

Then the old woman looked down at the dog.

"Hmm? What's this puppy. My goodness, how can it be so ugly. No wonder its owner abandoned it."

The old woman said this but still smiled as she stroked the dog's head and rubbed its chin.

At this, the young woman smiled warmly and said:

"Isn't it a truly stupid beast? How did it pick us out of all these people? Did it smell blood or something? It's quite fascinating."

"They say even dogs know people who like them. It must be some animal instinct. Here you go, your belly is so thin."

Xinpa, the White Hand Demonic Witch, threw a whole large croaker fish, and the stray dog that hadn't seen food in a long time wagged its tail so hard it might fall off and buried its head in it.

"Oh my, Xinpa. You shouldn't give fish to dogs. The bones might get stuck in their throat."

"That's just its fate. Besides, dogs by the sea eat fish just fine. Only country dogs that have never eaten fish get bones stuck in their throat."

"Hmm. Even Xinpa is kind to dogs."

At this, Xinpa burst out laughing.

"Of course. Dogs are much better than people. Aren't they excellent creatures that know gratitude and don't change, wagging their tails even to owners who boil them?"

"People say things like that, but I don't really understand. How can we know what dogs are thinking? Wouldn't it be strange if they suddenly turned and bit you one day? How can anyone but a dog know what a dog is thinking?"

Yun Yuanling looked down at the stray dog that was devouring the croaker fish.

Somehow her gaze was wistful, like someone recalling a moment from the past.

The dog must have been very hungry,

It devoured the large croaker in an instant, not leaving a single piece of skin, chewing and swallowing the head and tail and all.

And then it wagged its tail vigorously again and this time came to Yun Yuanling, making happy panting sounds.

Yun Yuanling slowly reached out her hand and gently stroked the dog's hard head.

"When I was young, I was really afraid of dogs. But now that I've become such a worthless thing, hmm, Xinpa is right. Dogs are better than people. At least dogs follow people who feed them. They don't care what kind of person it is, do they?"

"Most animals are the same. Come to think of it, people are much worse than animals. If only they were like animals, how much better the world would be to live in."

"Hmm. That's right. Xinpa, shall we stop this melancholy talk? It's about time, you should get to work, right?"

Yun Yuanling clapped her hands gently.

At this, people sitting at the roadside tables all over the street stood up at once.

And then, Yun Yuanling raised her long white finger and pointed to one side.

The straight line of Yun Yuanling's finger passed through the main street and led to the main gate of a huge estate.

It was the estate of the masters of Guangzhou, the Guangdong Jin Clan.

\begin{lstlisting}
	The chapter title is a reference to Overwatch's character Lucio's line. Feiwu 非武 or Bimu 비무 means 'non martial arts', essentially 'sparring'
\end{lstlisting}