\chapter{Let's Have a Spar (16)}

All sorts of medicinal herbs and vegetables had been thrown in, and it had simmered thoroughly overnight, so was there any way that the broth would be just any ordinary broth?

The aroma was already fragrant with a blend of bitter medicinal scents and the freshness of various vegetables, and as they boiled the rice, Master and disciple could only gulp their saliva.

Finally, the boiling porridge was poured into a bowl, and a raw egg was cracked and stirred in to complete the medicinal vegetable egg porridge.

Smiles spread across Master and disciple's faces. Soon after, they grabbed the spoons that had appeared from somewhere, blew on it for a long time, and finally put a spoonful into their mouths-

"Hmm."

"Mmm."

The expressions of Master and disciple were subtle.

"…You've had this before, right?"

"My Master just told me to eat elixirs or whatever, not this elixir soup. Ahem."

To be clear, the elixir soup was meant to be a bath to soak in, not a broth meant to be eaten.

Naturally, it was bland, plain, and had a bitter taste, combined with the fishy smell of various herbs and vegetables.

"Let's add some seasoning for now. Do you happen to have any salt?"

"Well, isn't that obvious?"

She did not know the reason why it was obvious to have salt on hand, but if she didn't know, she just had to learn.

Qing had a great realization.

\textit{I should always carry around rock salt and dried herbs.}

\textit{And some dried meat too. There isn't a single chunk of meat in this…}

It got better after adding salt.

Egg porridge is originally delicious just with whisked egg added to hot gruel and some salt.

Rather, the broth was fishy and bitter, ruining the taste, and a medicinal porridge that was just barely edible after making an ugly face was finally created.

"Hmm. It has a taste that's good for the body."

"The saying of eating elixirs like rice isn't a good thing. Elixirs should be eaten as elixirs, not as meals."

To be honest, Qing ate anything well.

This 'anything' included even rotten garbage or insects that would cause ordinary people to be sick, so she swallowed the egg porridge without a problem, despite it being just tasteless.

However, Tian Youxue, who was like a young master from a wealthy family as well as an old geezer, did not seem to do well, swallowing it with great difficulties.

Still, it was an elixir, so he had no choice but to swallow one bowl, but as it was with someone with a large, needless appetite, he had cooked a generous amount, and there was still a lot left.

Eventually, Tian Youxue, who had lost his appetite after just one bowl, put his spoon down.

Then, he watched in awe as Qing ate everything as if it was nothing.

It was a portion that four adults could eat two bowls full each, and with simple math, Qing ate seven bowls by herself.

Even in Qing's home, a world full of things to do, the spectacle of a beauty eating gluttonously, shoving food down her mouth without even tasting it was a popular attraction.

It was so outstanding that everyone had even offered money, encouraging her to eat more.

So for the primitive, ancient, uncivilized people of Zhongyuan who didn't have much to do, it was truly a new world and a spectacle they could only watch in a daze.

"You really were a beggar huh, but wow, how did all of that go in…"

"Oh, I definitely feel a surge of energy spreading through me now that this is nutritional porridge?"

"It's not a nutritional porridge but an elixir porridge. It's not 'like energy is spreading', it's actually spreading. Meditate and absorb it."

"Ah."

At that, Qing sat cross-legged, but due to her bulging stomach, it was too difficult, so she simply stretched both legs straight out and leaned back with her hands behind her.

This was because Qing's stomach was not a convenient, infinite pouch, and it would simply stretch as she kept eating.

Although she looked pretty sprawled out, Qing closed her eyes and observed her Qi and blood circulation.

It was a good opportunity to see how the elixir affected her monstrous body.

Recalling that she was different from others evoked an unpleasant sadness.

However, she needed to know how she was different in order to at least act as if she was the same kind of human or organism.

\textit{Hmm, I guess an organism would be fine, right?}

\textit{I'm not human, or a monster, or anything like that. At least I'm alive, so I'm not an inanimate object.}

\textit{Am I not? Are game characters inanimate objects?}

Suddenly, Qing's head dropped.

Perhaps it was because the elixir energy was too potent; her eyes felt sore.

\textit{Instead of thinking about all of this garbage, I should just look at my True Qi…}

The elixir energies penetrated the dantian and added themselves to each True Qi. Except for the True Qi that had already reached the Great Perfection and their maximum potential, they seemed to be adding equally to all of them.

At that moment, Qing used the Awakening Divine Arts, and the remaining elixir energies suddenly changed direction, focusing and
being absorbed into each individual True Qi.

\textit{If I just eat and leave it alone, it spreads equally to all True Qi that have not reached Great Perfection, but if I eat and meditate, it adds to the Inner Energy Cultivation Method that I am channeling at the time.}

\textit{Then how about other people…?}

"Master? Is it always like this with elixirs?"

"Heh. If you don't tell me what you mean by 'like this', how am I supposed to listen and say if it's right or wrong?"

"Uh, I'm not really good at explaining, but how should it be normally?"

"The natural energy contained in an elixir spreads toward the extremities of the body, leaving about one out of ten in the meridians, and the rest leeches out through the skin."

Therefore, one must use Inner Energy Circulation to grasp the elixir energy and collect it in the dantian before it fully leaches out.

The difficulty of this absorption varied depending on one's skills in controlling True Qi and also on the Inner Energy Cultivation Method they have learned, and it was extremely different even for every type of elixir.

"That's why martial artists are always yearning for a Divine Arts. Even if they consume the same elixir, the results are different. And the better the elixir, the easier the absorption and the less burden it puts on the meridians. Is there a reason why the Great Rejuvenation Pill is the Greatest Elixir Under the Heavens?"

The energies that remain in the meridians, about one out of ten of the elixir's energies, were not necessarily beneficial, and if their properties were rough, they would rather destroy the meridians and harm the body.

It was because natural elixirs had these properties that people went through the trouble of reining them into pills despite the loss of energy.

"Well, it seems you absorbed everything since you're talking, right? It doesn't even have much natural energy in one bowl anyway. I'm going to catch up on the sleep I missed outside, so soak in it and absorb it."

"Are there any other precautions?"

"According to the prescription, it stings a bit. But it's not to the point where you can't endure it."

Qing narrowed her eyes.

"Are you sure this time? You said it's stinging, not painful, right?"

"I'm just telling you what's written; how am I supposed to know when I've never done it myself? Based on the theory of martial arts, it probably stings a bit, right?"

Originally, an elixir's natural energy, when eaten, spread from the stomach, the center of the body, outwards and leached out through the skin.

However, the Awakening Divine Arts was a unique Inner Energy Cultivation Method that could absorb energy not through breathing, but also through the entire skin.

Of course, it was only unique and its efficiency was a mess, not even half of half of half of half of half of the breathing method.

It was an idea to just soak in an elixir since the skin's absorption rate was trash.

The practice of absorbing an elixir's energy through the skin using this Awakening Divine Arts was called an elixir bath.

Naturally, it could only sting due to the energy penetrating the skin.

"According to the records, it's said to feel rather refreshing once you get used to it. Why don't you try it and tell me how you feel. Haiyaa, I'm so tired I could die. On top of that, I still need to continue Disjointing the Bones, and what's even scary about it."

"Disjointing the Bones?"

"When did I say it was Disjointing the Bones? I said it was Flowing Flex. Have you already gone deaf, you green girl?"

"That's weird. You definitely said it…"

"Ha. People will be scared if they hear that. Where in the world would there be a Master who would do Disjointing the Bones on his disciple?"

"Hmm. Maybe I misheard. I'm sorry."

Since Tian Youxue was so confident, Qing simply thought she had misheard.

"One bottle of that is two hundred gwan. One drop is worth tens of mun. Be careful, don't waste a single drop."

Tian Youxue requested while heading outside.

After hearing that one drop was worth tens of mun, she realized anew that this was truly no ordinary extravagance.

And so, Qing carefully dipped her body into the bath.

The bath came right up to her chin, and she felt itchy and a wave of itching came all at once.

But that was for a moment.

After she began circulating the Awakening Divine Arts, a sensation as if her whole body's skin was being burned hot began, similar to a carbonated beverage entering her mouth.

But that was all.

It wasn't to the point where she couldn't bear it, but it was awkward to keep her mouth shut. It was like when she gulped down a huge glass of carbonated beverage in one go, painful and stinging, yet at the same time strangely cool and refreshing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After sucking and absorbing until no more energy could be absorbed, much time had already passed, and it was already dark.

When she checked her achievements in the Martial Arts Window, she had reached the Eighth Stage in one go.

\textit{Wow, wow. So this is what people mean when they say elixirs are good.}

Qing's Inner Energy Cultivation Method's achievement was simply determined by the total amount of Inner Energy gathered by that
method, so she had reached a high level unusually quickly. 

Only Tian Youxue, not knowing the reason, was in awe.

"Eighth Stage? What the hell."

\textit{So was this why it had been repeatedly emphasized for generations that one should take on a disciple with good talent?}

Tian Youxue roughly understood it that way.

After all, what is good, if not good?

"Alright. How is it? Does it feel like your body has awakened?"

"It still stings, though…"

It felt like she had peeled a layer of skin off after aggressively scrubbing herself.

Her whole body was just sore, hot, and tingling, but at the same time, it was also extremely refreshing.

"It's probably because the secondary meridians in your skin have become dull to stimulation. Now, after you sleep well, you'll realize why the Awakening Sense Method is called the study of awakening the body."

"Ooh. Isn't it the Awakening Sense Divine Arts?"

"It's Awakening Sense Method? I gave you the Secret Manual, didn't I?"

"But the title is Twenty-One Day Night Training. There wasn't anything about that in the Sutra either…? Where is the line that says to awaken the body in the content about feeling the low of heaven and earth with your body?"

"Aren't sutras usually just written with big words or something? That way, each person can complete it little by little with their own mental imagery."

The reason why martial arts sutras are vague is because they also intentionally did not force a specific form that each individual had to complete.

"I thought it was a Divine Arts, but…"

She thought it was the Awakening Sense Divine Arts, but it's the Awakening Sense Method.

\textit{No wonder it was gold.}

Qing swallowed her words inwardly.

Somehow, she felt like she was greatly tricked.

"A Divine Arts is a Divine Arts. Does it only become a Divine Arts if it's written as Divine Arts? Now, go and sleep well."

"What does that mean?"

"For a Divine Thief and all martial artists, what's they dream of if not a sharp sense? Even if the Awakening Divine Arts is third-rate at accumulating Inner Energy, if we consider just the efficacy of awakening a sharp sense, then you can say it's an unparalleled Divine Arts, the best under the heavens. You'll feel even the slightest breeze vividly. You'll understand just how amazing the feeling of feeling the flow of heaven and earth is."

"Ooh."

Qing's eyes shone.

\textit{Even though it's a golden martial art, it has such a function?}

At that, Tian Youxue chuckled and then spoke, "Ahem."

"The Martial Arts Tournament starts tomorrow, right. You'll probably be busy too, so I guess I'll go sell some tonics. Let's meet again in eight days, when we go to the Flowing Flex second session. How do you want to do it, one shichen or three?"

Recalling the terrible pain, the focus in Qing's eyes disappeared.