\chapter{Let's Have a Spar (12)}

Qing returned to Wucheon Pavilion and raised both Strike-Step Flash Movement and Flowing Flex Technique to the first mastery level.

She had already reached level six mastery in Shadowless Divine Hand, and when it came to internal energy techniques, there was no need to waste cultivation points if she was going to learn it properly anyway.

By nature, she would've maxed out internal energy techniques first—more is better, the bigger the better, the grandest is the best—and then dumped the rest into lightness techniques.

But lately, she hadn't been slicing up many villains, so her cultivation points were basically stagnant.

The cultivation points earned through pure training were pitiful, and even then, they only meaningfully raised the specific martial art's training level—free cultivation points were just a bonus at best.

That's why Qing was being extremely cautious with what little she had left.

It was the same principle as with money: when people are flush with cash, they splurge without thinking, but the moment their purse runs dry, even one extra coin for a soup with a few more pieces of meat becomes a matter of intense internal debate. 'Is it really worth it? Should I just get another dumpling instead?'

That kind of thing.

Anyway, just reaching first mastery meant the martial art's mnemonics would invade her mind and completely take over without permission.

And that was enough for her to show off to Tian Youxue: Look at me, your disciple is incredibly talented!

By that time, it was already late at night.

After all that chatting with Tian Youxue, it was less like a lesson and more like two people who got along too well goofing off together. All she really got out of it was some martial arts manuals.

"For the time being, train with the Scholar of Instruction."

"Won't Master be lonely, though?"

"Lonely? Please. Do you think an old person who's lived this long doesn't know hundreds of people? Of course I've got things to do. That brat Tian may act crass, but as a Scholar of Hanlim Academy, he's one of those giants who's read at least a thousand cartloads of books. This is the perfect time for you to build some academic knowledge as well."

"Academic knowledge? But all a martial artist needs is sword skills—what's the point of academics? Hmm. Although now that I mention it, I kinda want to try eating at the academy dining…"

"…That damn appetite of yours."

Ximen Surin let out a chuckle.

"Well, that's enough of your evening greeting. You may go now, disciple."

But Qing lingered, shuffling her feet as if she had something to say, eyes darting around instead of leaving.

"Hm? What's wrong? Why aren't you off to bed?"

"Master, um… so, I was wondering…"

"There's nothing to wonder, I'm sure, but go on. What is it?"

"Well… is it… maybe… would it be okay… if I sleep with you tonight…?"

"Hm?"

One of Ximen Surin's eyebrows rose.

That was quite the indecent and disgraceful thing for a fully grown, adult disciple to be saying.

But then, seeing Qing fidget anxiously and peeking up at her, she suddenly realized:

\textit{This foolish girl has fallen into Inner Demon!}

Her mind and spirit were worn down, and she was aching with loneliness—a craving for warmth, a hunger for affection.

It was the kind of inner demon that plagued rootless wanderers who had nowhere to return to.

But then again… wasn't it because the Divine Maiden Sect had failed to be a warm home to its disciple?

And that brought up a moment of regret in Ximen Surin's heart.

Just last winter—how had she treated her?

That foolish child always wandered around with a silly grin, so she assumed everything was fine.

Technically, it wasn't one of the more dangerous types of Inner Demons.

But if it wasn't resolved properly, Qing would eventually find herself at the crossroads of extreme emotional attachment or utter emotional detachment.

She would either become a foolish good-natured person who wagged her tail at everyone, unable to distinguish right from wrong—or a cold-blooded woman who walked around with a frosty face and zero interest in anyone else.

Ximen Surin forced a warm, gentle smile.

"Very well. This old woman happens to have an empty bed beside her. Come here then, let me hold my lovely disciple."

"Heehee…"

Giggling like a child, Qing did what she always did—she pulled down her outer robe like it was some shed skin and crawled under the covers.

Ximen Surin's forehead veins twitched again.

This damn girl—still flinging off her clothes like it's nothing, parading around in that shameless posture! She hasn't fixed that disgraceful habit yet!

But then again, this was a girl suffering from a Inner Demon due to emotional starvation—and that made her heart go soft.

Ximen Surin clenched and unclenched her fist, seriously debating whether she should discipline her or not.

But in the end, she missed the window to do it, and all she could do was sigh deeply and gently wrap her arms around her disciple as Qing nestled into her chest.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

They had breakfast together the next morning.

Oddly enough, Ximen Surin didn't say anything even when Qing started swinging utensils at the table like a savage—but that was only because she had already been told about Blade-Life Training.

Since Qing had dragged martial arts into her daily life, it might've looked improper, but her dedication was worth acknowledging.

As long as she didn't do it in public, it wasn't a problem. For Ximen Surin, who always emphasized elegance and grace, it was a way of thinking she could never adopt—but she respected it nonetheless.

Of course, after getting badly cut once, Qing had become somewhat more cautious. She wasn't as wildly thoughtless anymore.

Then, right after breakfast, she headed for the bathhouse—because of what Tian Youxue had said the night before.

As soon as she entered, the air was smoky and choking, the stench acrid enough to punch her in the face. The stench was so foul it stung her eyes.

"Ugh, Master, what the hell did you do to the bath?"

"External body techniques are supposed to be nasty. You think softening the human body is an ordinary task? It's all about the medicine. There. That medicinal bath is for you."

Tian Youxue sounded congested as he spoke.

Understandably so—his nostrils were plugged with cloth, and he had a clip pinching the bridge of his nose.

Following his pointing finger, Qing turned her head—and there it was, a disgusting tub of bubbling green smoke.

"You… want me to go in there? That color shouldn't exist in this world."

The smoke was green, but the water itself was a vivid purplish-red.

"At that level, you should be grateful. Ever heard of Iron Sand Palm? It's the most famous external art in the world."

Iron Sand Palm was known for a brutal training method that involved jamming your hands repeatedly into red-hot iron sand.

If you mastered it, your hands reached the level of Diamond Body and became jet-black, even leaking metallic poison.

"What, did you think training external martial arts was like studying—just sitting and breathing and circulating energy? Most of the time, it's blood, sweat, and tears. Even for External Divine Art, it all boils down to the same four methods combined."

The first among external training methods was abuse.

Destroying specific parts of the body completely.

And the second—was torture.

Beating, burning, twisting—if not for the fact that the desired outcome was on the recipient's side and not the torturer's, it wouldn't be any different from actual torture.

And with Poison and Medicine, that made four methods total.

"So, if all you have to do is soak in a medicinal bath and endure it, then among external body training methods, that's pretty much paradise."

"I feel like I'll actually go to paradise if I get in there. And isn't that stuff… literally boiling right now? Are you trying to make stew out of your disciple?"

"It's not boiling because it's hot, but because there's a shitload of herbs in it. The temperature's perfect. If you soak all the way in, wow, back in my younger days I used to train in it all the time. It's so sticky and squishy, it feels absolutely filthy, like you're wallowing in a damn sewer."

Tian Youxue didn't even bother to hide his laughter. He cackled out loud.

"You'll understand once you get in. That wretched texture alone is enough to make you swear. There isn't a single part of it that isn't nasty. If you're bitter about it, go get yourself a disciple one day and do it to them."

"That's literally just inheritance of resentment."

"Exactly. That's the affection between thieves. By the way—have you memorized the Sutra for the Awakening Sense Method yet? Your master said one night was more than enough for you to learn it."

"I just need you to do True Qi Daoyin\footnote{True Qi Guidance} for me once."

At that, the Divine Thief scowled.

"What, you think True Qi Daoyin is something you get from the neighbor down the street? Do you have any idea how hard that is? You really are a damn little thief at heart."

"Well, I've never done it before, so how would I know? Hehe. But didn't you say I'm supposed to become the ultimate thief of the world? So this is fine, right?"

"Ghh… That thing leaves me drained for three whole days."

"Aw c'mon, Master. Just once. Just this once."

"Hrgh…"

That kind of cutesy act wouldn't work on Ximen Surin, but it was deadly effective against Tian Youxue.

In the end, Tian Youxue grumbled as he pressed his palm flat against Qing's back, now sitting in a meditative pose.

True Qi Daoyin was no easy task.

It required directing someone else's internal energy through paths that didn't originally exist in their body. Even Ximen Surin, a master at the Profound Realm, had sweat buckets after guiding Qing's energy while teaching her the Zhu Xiangs Heart Cleanse Mirror.

For Tian Youxue, a master of the Unrestrained Realm, it was the kind of grueling work that really did drain his body for three whole days.

But, well—what could he do? His disciple was pretty and knew how to work him.

All of his other disciples at Hanlim Academy were fully grown, half-witted men who didn't even understand the basic tenets of the Hundred Schools of Thought and just spouted dumbassery.

For the record, Tian Youxue was a giant among the scholars of Hanlim Academy—the equivalent of a top university professor by modern standards—and he regarded disciples the same way professors often regard students.

So Tian Youxue finally managed to guide Qing's energy through a full meridian cycle along with the incantations for the Awakening Sense Method.

"Haaah, there's no way I'm doing that again. I'd rather die."

Tian Youxue collapsed onto the floor of the bathhouse with a groan. His clothes were soaked through, and it had only taken about half an hour.

Meanwhile, deep in Qing's lower abdomen, her dantian welcomed a brand-new resident.

The worldly energies she'd taken in through breath had condensed into a faint wisp of genuine internal energy—this was the Awakening Sense Qi of the Awakening Sense Method.

It swept once through her body, checking out its assigned zone, and returned—only to discover that the "private room" it expected to move into was actually more like a cramped dormitory packed with other tenants.

And not just an ordinary shared house, either—there were no walls, no partitions. Just a messy military barracks stuffed to the brim.

At this point, even if it said, 'Uh, sorry, I'll just leave', it had already become internal energy. If it dissipated, it would become scattered Qi and cease to exist. That would basically be death.

It wasn't like it could just say, 'I'd rather die than live with these people!' and off itself. So it timidly lingered at the entrance of the dantian, trying to read the room.

Currently, since Qing hadn't shed blood recently and her internal world was calm, the Daoist and Buddhist energies were having a field day, lounging around and lazily scratching their bellies.

On the other hand, the demonic energies, starved of bloodshed, were sulking off in a corner, sitting cross-legged in gloomy silence like a bunch of sorry rejects.

And in the farthest, darkest corner—there was a grotesque, pitch-black demonic Qi, bound tightly, glaring around with eerie, bulging eyes like mold incarnate.

This new Qi belonged to the Yin attribute, mild in power and geared more toward bodily refinement than energy accumulation—making it too ambiguous to be called fully righteous or demonic.

Which meant it had to suck up and play nice. So, the Awakening Sense Qi hesitantly looked around and then gravitated toward the strongest group.

The Daoist and Buddhist techniques gave the newcomer a once-over. Then, with a single nod and a slight chin gesture, they pointed to a spot.

The meaning was clear: We don't really like you, but we'll tolerate you.

So the Awakening Sense Qi awkwardly settled into the lowest seat at the table.

Just then, Blissful True Qi—the demonic Qi of the Blissful Maiden's Technique, which had recently been driven to a limb of the body for misbehavior—began poking the new guy.

'Are you demonic? No?'

'Should I purify you? Maybe not?'

Then, the two strands of Qi locked eyes.

"Huh?"

Qing tilted her head.

\textit{What was that? What is this weird… feeling?}

She had this vague, strange sensation—but no matter how hard she focused, she couldn't pin it down.

That feeling… like something she'd experienced before…

"Hnnngggh, I'm dying. First-level mastery, huh? Then soak yourself in there already. Ugh, I feel like I aged a hundred years…"

Tian Youxue groaned and crawled out of the bathhouse like a defeated soldier.

"Huh? Where are you going?"

"I may be a thief, but I'm not shameless. What, you think I'm gonna sit here and gawk at my naked disciple?"

"Didn't you already do enough shameless stuff, like handing me a literal erotic manual?"

"Kukuku. I suppose that was shameless. But a man ought to have a little shamelessness. If he's too uptight, he's basically a eunuch. But even so, would I really peep at my own disciple? Breaking the natural order is no different from being a beast."

"Can't you just, like, turn around or something? If you leave, how am I supposed to train on my own? All I have to do is soak in it, right?"

"What kind of girl has no sense of caution? Never trust a man like that. The world is crawling with beasts who just happen to be men."

"Aw, but you're Master."

At that, Tian Youxue let out a soft laugh.

\textit{Man, how does she talk so sweetly?}

"I'll just be over there, behind the floor vent. Just talk to me if you need anything. Shit stinks so bad in here I can't take it anymore."

The 'floor vent' referred to a small ventilation window down near the floor.

After Tian Youxue left, Qing stood in front of the bath.

Even from afar, it looked terrifying—but up close, it was downright hellish.

It boiled and bubbled like lava, and thanks to its viscous consistency, even the bubbles popped slowly. Just looking at it made her feel like it'd strip her flesh and leave no bones behind.

Was this what the baths in Hell looked like?

Qing shouted.

"Are you sure it's safe to go in!? It looks like it'll kill me!"

A voice echoed from the other side of the floor vent:

—That one tub is packed with enough medicinal ingredients to cost three gwan of gold. If I wanted to kill you, there are cheaper ways. Just soak already. You'll live.