\chapter{Let's Have a Spar (9)}

The daily life of the Leader of the Wulin Alliance is busy.

At least, that's what the Leader of the Wulin Alliance liked to believe.

But the people around him thought a little differently.

All the Leader really did was greet guests, eat with them, drink tea, snack on sweets, and chatter the day away.

Then, once the sun set and visitors stopped showing up, he'd finally pretend to work—going 'thump, thump' as he stamped documents with his seal.

So, wasn't this all just cruel and unusual punishment?

Cao Xuanliang spent his entire workday on hospitality he never wanted, and once he finally got to eat dinner, he had to spend his precious personal time buried in bamboo scrolls.

There were only four days left until the Wulin Tournament. Once tonight passed, only three.

After the tournament ended, things would calm down again. Then, at last, he could resume the training he'd put off in preparation for the event.

Yes, he would enter closed-door cultivation for a whole month.

The tournament would be over, so even the Leader of the Alliance deserved to train a little.

The Leader of the Wulin Alliance was still a martial artist, after all — a warrior!

Dreaming of secluded training after the event, he stepped out of the Alliance Leader's Hall with a bloated stomach full of tea.

"Hey there, Cao Xuanliang."

A chill ran down Cao Xuanliang's spine.

A person's voice doesn't change all that much with age. Unless they're one of those lazy bastards who puff on hemp leaves or whatever. Most people don't.

He recognized the voice immediately.

"Surin? Didn't you say you weren't coming? I heard it straight from that girl, Ximen Qing…"

"I wasn't going to come. But it felt pathetic, an old woman barging in like she still mattered. I was still torn, so I snuck in quietly."

Cao Xuanliang's face twisted.

"Goddamn it. Everyone else uses the excuse of ‘pathetic old age' to stay home and put their feet up! But I'm the only one playing Alliance Leader, still raising hell in my old age!"

Ximen Surin scoffed coldly.

"Hmph. You brought it on yourself. Didn't you see this coming?"

Cao Xuanliang felt bitter. Deeply bitter.

\textit{And who the hell's fault was that?!}

But he couldn't very well admit that he'd tried to block her from becoming Alliance Leader.

Then he caught a good look at Ximen Surin's face—and flinched.

What the hell? That old bat looked even younger than before.

If she was at the Hyungyeong level of martial arts, then looking younger meant she'd achieved a major breakthrough.

"Are you already looking past the peak of Profound Realm?"

In other words, had she reached Mid-Stage Profound Realm?

Last he heard, she was in Early-Stage Profound Realm, and that was twenty years ago, back before she holed up inside the Divine Maiden Sect, never to emerge.

"It's been about seven years. Once I broke through, I started to realize how damn impressive that bald old monk Wunue really was. At this level, each step forward isn't just a step—it's a goddamn cliff. I don't think I can go any further. I'm not the right material in the first place anyway."

Ximen Surin's expression soured.

That bald old monk 'Wunue' was none other than the Grandmaster of Shaolin—the man considered the strongest martial artist alive.

"Hmph. So that's why you raised a disciple instead? I've seen that girl—nowadays she's apparently dragging all her little friends together to train every single day. Where'd you even find a sweet kid like that? I didn't think you had it in you to raise a  disciple."

"Really? That kid?"

Ximen Surin's lips curled softly.

Cao Xuanliang's expression was a mix of envy and irritation.

At their age, if you weren't bragging about your kids, all you had left was your disciples.

"Hey… you wouldn't happen to have a secret method for fixing personalities, would you? My great-grandkid is completely obsessed with chasing girls, and no matter how much I scold him, it's useless. That girl Ximen Qing, she's shockingly well-behaved."

"She's always had a good heart. Brave too. Even facing two masters far above her, she stood firm and shouted against injustice. That's why I took her in."

"Hmm. Still, you must have done something."

"Back then, just like now—the best thing to give to a kid who won't listen is a harsh scolding."

Cao Xuanliang snorted.

Still, she had mellowed out with age. That old lunatic never used to talk like this.

She used to say, ‘If the brat won't listen, beat him within an inch of his life.'

Now she was saying, ‘A sharp rebuke is best.' Playing the dignified old master.

And she'd even stopped saying that thing she always used to mutter—about how 'a man only comes to his senses when beaten at least once every three days'.

Maybe that mellowing was why her cultivation had improved.

"But why are you here now? From what you said, you weren't even planning to show your face."

"I'm thinking of proposing a topic for the Wulin Tournament. Yeah. How long are we going to keep ignoring those Black Spot bastards? They're a plague on the world. Shouldn't the Wulin Alliance step in and clean them out?"

"…The hell's this about the Black Spots now?"

Cao Xuanliang's face soured.

Sure, those bastards had stirred up some real filth. But did they really need to be cleaned out? It was a gray area.

Human trafficking, stolen goods, selling human meat—disgusting, yeah, but if you let the roaches all gather in one place, at least they didn't spread elsewhere.

Plus, they were the only place left where you could openly buy goods banned by the government.

"The psychos put a bounty on my disciple. Said it was ten thousand coins or something."

"…Ugh."

Cao Xuanliang groaned.

\textit{Why the hell would those lunatics poke a sleeping mad dog?}

Still, Cao Xuanliang couldn't decide Alliance policy alone. And, truthfully, it wasn't a topic he was thrilled about.

So instead of giving a clear answer, he changed the subject.

"Let's talk about that at the tournament. I already gave your disciple Wucheon Pavilion, so go spend some time with her as master and student. No need to start bringing up grim topics before the event even begins."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

By now, Qing's wound had completely stopped bleeding. All that was left was the dull, lingering pain.

It looked mostly healed—if you didn't know better, you'd think it'd been two weeks already.

Turns out, 'inhuman vitality' came with superhuman recovery too.

Still, Tang Lan-Ah, speaking in her role as a healer, said not to get complacent.

Better to observe longer than get caught off guard.

But Qing definitely felt like she'd been caught off guard.

She'd gone days eating nothing but honeyed goat milk, then honeyed water, then honeyed cow milk. What the hell was with all the goddamn honey?!

Even the smell of it was torture now.

So when she finally got to eat something else—for the first time in six days—it was a tear-soaked banquet.

A full-blown royal feast in her eyes.

Even if it was just porridge.

"What, is it really that good? Your eyes are bloodshot."

Qing nodded furiously.

\textit{Food needed salt, dammit.}

\textit{Sweet, spicy, rich—it didn't matter. All of that had to start with salt!}

\textit{Food needed to be salty! Sweet food was a sin!}

And now, finally getting to chew again, she understood from the bottom of her heart why teeth were considered one of the five blessings of life.

It was a thin porridge, boiled down until the rice grains nearly melted, with dried seafood tossed in and extra water added to thin it even more.

But to Qing? It was paradise.

Only after her heart stopped pounding was Qing allowed to start sparring again—on the condition that she take breaks when it flared up again.

Now, even without her, they could happily spar among themselves, so Qing, stuck in the corner carving radishes, found herself feeling… a little left out.

And to make matters worse—there was absolutely no progress in her carving!

This was impossible. Just impossible!

You can only start enjoying something if you're making at least some progress.

The status window might boost physical stats, but it did nothing for mental or artistic sense, which meant Qing's abysmal sculpting instincts were still fully intact.

Outstanding physical senses were just tools. And just because you had good tools didn't mean you were suddenly an artist.

It all came down to the talents people were born with.

Of course, the universe was unfair like that—people good at one thing were often good at everything else too. Disgusting.

In the myths of Zhongyuan, people were divided into those carefully crafted and those slapped together in a rush.

According to legend, the goddess Nuwa, who created mankind, first molded people one by one in her own image, making each one beautiful and refined.

But eventually, she realized 'Wait, this is ridiculous. At this rate, how am I supposed to fill the whole world?'

So she gave up, grabbed a rope, dipped it in mud, and flung it around.

The splattered clumps of mud turned into people.

The mud that hit Qing clearly had no aesthetic particles in it.

Even with her incredible physical sensitivity, all she was good for was making food-scrap disasters.

After wasting perfectly fine radishes day after day, she finally let loose. And Qing wasn't the type to hold back just because her tongue still stung a little.

So she ran wild—rolling, leaping, getting smacked, pretending to rest when Tang Lan-Ah nagged, then charging in again.

She kept her win rate barely above ten percent, but it'd been a long time since she'd worked her body this thoroughly.

On the way to the bathhouse, she bowed politely to Tian Youxue, and after getting squeaky clean, she burst into the guest hall—throwing the door wide open.

And there sat a guest, who had taken a seat without so much as a notice.

They looked at Qing—and Qing's face bloomed into a full blossom, radiant and delighted.

"Ah! Master!"

Without even kicking off her shoes, Qing dashed forward and leapt into the air.

She dove straight into her master's arms and refused to let go.

"My, my. A grown woman with no shame—what's with this disgraceful display?"

Ximen Surin said so, but the corners of her eyes crinkled with joy.

"Hehe. I missed you."

"Hmph. As if you've been gone that long."

As she stroked her disciple's head, Ximen Surin tilted her head slightly.

\textit{Was this girl always this affectionate?}

Well, affectionate—sure. Qing had never been shy with her master and always clung to her. But… had she ever been this clingy?

Even though Qing had never been distant, there used to be a subtle restraint when it came to physical contact. Or so she remembered.

But Ximen Surin let it slide without much thought.

Maybe the child was just slowly learning what affection meant, after growing up all alone.

"So, I heard you've been training very diligently. Have you made any breakthroughs?"

"Mm, well. Lately, I've been training in the Subtle Mysteries of Softness."

"Good! Very good. Your martial balance was always a bit too aggressive. Did you manage to obtain the Tai-Chi Flowing Sword?"

"Not yet. But I did end up learning the Sovereign Sword Form somehow."

"Oh? Picked something up, did you?"

"Well…"

It was a strange conversation.

Talking about 'picking up' sword techniques, or 'not yet' mastering this or that—anyone listening in would've stared in stunned disbelief.

Then it happened.

Ximen Surin, who had been gradually focusing on her disciple's mouth, finally confirmed what her eyes were telling her.

"…Disciple? Your mouth… your tongue—what in the world happened? What is this?"

"Ah. I, uh, cut it. While training. Oh right! Have you heard of Blade-Life Training? It's part of mastering the Subtle Mysteries of Softness…"

Qing, having completely forgotten Tang Lan-Ah's warnings, started chattering away.

She excitedly explained how a master—presumed to be the Divine Thief—had given her advice, how hard she'd trained, and how it had all led to this unfortunate incident—

SMACK!!

"AAAGH!"

Qing grabbed her head and went tumbling across the finest rug in the finest room of Wucheon Pavilion.

\textit{Ow, ow, OW!}

Even when she cut her tongue, it hadn't hurt this bad. That time she was so embarrassed she just lowered her head and covered her mouth.

But when struck by Ximen Surin's thermonuclear palm, there was no room left for pride.

All thoughts vanished, leaving only pure, raw pain. It's almost like reaching nirvana.

"Hnnngh, seriously… that hurts so bad…"

A single teardrop rolled down from Qing's eye.

This was the one and only moment when Ximen Qing shed tears.

"And what, exactly, made you think ruining your tongue was something to boast about in front of your master?!"

Ximen Surin's forehead was still pulsing with veins.

"Haaah. Stick out your tongue."

"Yes, ma'am…"

Qing obediently stuck out her tongue.

Well, 'obedient' in her own way.

No matter how she meant it, there was no dignified way to stick your tongue out in front of your master.

"…What in the world. Can it even move properly? You don't seem to be lisping. Can you still taste things? You always did love your food…"

Ximen Surin's voice was full of concern.

Qing gave her a confident little smile, trying to reassure her.

"No need to worry! Lan-Ah said that since tongue muscles are naturally split bundles, there's no problem! Oh—check this out. I can even move it separately!"

With that, Qing showed off a tongue that was split about an inch at the tip—wriggling it in a way that was downright obscene.

Naturally, this was not something you showed your master. Especially not a master whose forehead veins were still throbbing.

She was asking for it.

SMACK!!!

Qing froze in place, her mouth still open.

She had just learned a harsh truth:

There was a level of pain beyond pain, a threshold where you couldn't even roll on the floor anymore.

You just stood there, like a statue—paralyzed in pure, holy suffering.