\chapter{Let's Have a Spar (6)}

Qing narrowed her eyes.

"Far as I know, there's only one person in the world dumb enough to barge into someone else's guest room uninvited."

"I knew it! That sword bitch came by last night, didn't she?!"

"No. You. I meant you."

Still, what stuck with her more was that whole 'cliché seduction stunt' line.

\textit{Is that really a thing? Is tearing each other's clothes some common girl-on-girl thing now?}

"It was me. Tried getting dressed with the dagger instead of my hands. Didn't work out great."

"Why the hell would you do that?"

"Yeah, good question. Why am I doing this…?"

If the dagger weren't quite so sharp, this whole thing wouldn't have been so hard.

But it was the Azure Blade, wasn't it?

As befitted a renowned legendary weapon, the moment even the slightest bit of fabric brushed the blade under its own weight, it would slice straight through without resistance.

In the end, she had to keep the cloth at a perfect angle where no pressure touched the blade, and gently pull it toward herself with just the very tip.

But the edge was so sharp that nine times out of ten, the fabric got pierced and dragged the blade all the way down to the hilt—brushing along the back of her hand with a whisper-soft stroke.

Then when pulling it free, the blade would slide deeper again, widening the tear even more.

After ruining one full set of clothes and spending the whole night practicing, she finally managed to get dressed properly by morning.

"But wait—how'd you know I'd be coming and have me run this errand?"

Then Tang Lan-Ah suddenly screamed.

"Qing! You can't go outside like that! You so much as move and you'll flash everyone!"

"…? Obviously, I wasn't planning on going out like this. What do you think I am?"

"But! You walk around butt naked at the Divine Maiden Sect! Like, all the time! You've got that… showing-it-off kind of hobby. Even when you sleep. Ah—don't get me wrong! Baihe walks around with her tits out all the time too, okay? I totally get it. Nothing wrong with it! Great, even! Supportive! Thanks!"

"What are you even talking about? And when did I ever walk around naked at the sect? I definitely wore clothes. My master made those herself, okay?"

"Yep! Yep! You're right! Of course, Qing, you're totally right. If you say so, then that's how it is."

"God, you're pissing me off…"

"Ah! Still, I'll go grab them right now, so seriously—don't go out like that, okay?"

"Hey!"

Tang Lan-Ah had the last word, infuriating Qing even more before bolting out the door.

Hemp and rough linen were the cheapest fabrics you could find in Zhongyuan.

Thick-threaded and coarse, they didn't feel great against the skin, but they were extremely durable and hard-wearing.

Fun fact: hemp clothes were woven from cannabis plants.

Still, they were notoriously hard to take care of.

They stained easily, the dirt wouldn't come out, and once they got creased, the folds would hold like iron. Practically impossible to smooth out.

So the people of Zhongyuan got clever about it.

Hard to clean?

Then just don't clean them.

Stains won't come out?

Then just don't bother.

Thus, hemp clothes were usually just worn until they fell apart—commonly used as work clothes.

No proper laundry involved. You just dunk them in water, wring them out, and hang them up.

So after a few years of that, the fabric would turn jet-black and develop creases all over. That's why people in old paintings looked so shabby—they were wearing worn-out hemp.

Thanks to that, Qing felt way more relaxed slicing up this kind of "throwaway" martial robe.

On top of that, the rough, tough material actually caught better on the edge of the blade. Easier to maneuver, and much more forgiving of mistakes.

So Qing leveled up—dramatically. Within just half a shichen (about one hour), she managed to get fully dressed without a single hole in the fabric.

Considering she'd spent the entire previous night sawing apart one training robe and had only succeeded in dressing herself twice, this was a huge win.

Chin high, smug as hell, Qing thought, \textit{Hah! This is nothing!}

Next on the agenda: breakfast.

Thankfully, breakfast was manageable—dumplings, stir-fried veggies, and soup.

Dumplings could be lifted with the dagger and just popped into her mouth. The veggies were tangled together, so stabbing anywhere got her a whole chunk. And soup? Please. If she could lift loose slabs of meat with no balance, a heavy bowl was child's play.

Sure, any normal person's arm would be trembling from the weight, but Qing was the kind of monster who could eat soup with a cooking pot balanced on one finger.

Still, it didn't change the fact that she was putting in serious effort.

Watching this spectacle, Tang Lan-Ah eventually couldn't hold back.

"Can't you just eat normally, please?"

"Aside from eating and dressing, all I do is train. If I avoid it just because it's hard, I'll never get it. Gotta stick with it until it becomes natural."

You couldn't really argue with sound logic like that.

But it still made you feel kinda bitter.

Like when a friend tells you, 'Why are you falling asleep with a book open?'

'Even one line of sage wisdom is worth more than sleeping all night.'

You've got no counter, but it still makes you want to punch them. 'Who the hell are you to talk? You don't even read that much!'

Same thing now—Tang Lan-Ah's face scrunched up in a sulk.

\textit{When had Qing ever been so obsessed with training, anyway? And now she was being dramatic about it during breakfast?}

But what could Tang Lan-Ah really say?

Even if she stormed off in a huff like yesterday, she'd probably end up regretting it later—letting that Gong Sun-Yaoyi bitch have her moment.

That's why she came bursting in first thing in the morning today.

After breakfast, Qing claimed a spot at the training yard and slowly started running through the forms she knew, stretching her body.

Tang Lan-Ah lounged nearby, propping up her chin, chatting out of boredom.

"Oh, right. Lan-Ah—do you know Lady Xue Iri?"

"Huh? You mean the Ice Flower? Sure I know of her. Everyone does. But I don't think she's close to anyone. Why?"

"Oh, nothing. I saw her once, and she's seriously stunning. Did you see that beauty mark under her eye? She's got this serene vibe, but that one little mark. Wow."

"What the hell, you're sitting next to a beauty and still talking about some other beauty? Hey, what's this? Guess what I'm doing."

"Please tell me that's not a flower pose."

"Why not? I'm literally the Poison Flower. I'm holding up a flower, so clearly, I am the flower support."

While they were joking around, as usual, Nan-gong Shencai arrived—just as punctual and consistently present as ever.

"Sword Sister? Hm. Are you in mourning? My condolences."

"The hell? Why're you acting like someone died?"

"You're wearing mourning clothes. I thought perhaps you were grieving. Though I suppose if you're short on coin, it's not like you can afford a new outfit—"

"I didn't buy this because I'm broke, okay? It's part of my new training method. Still, thanks for the concern."

"A training method of… dubious effectiveness, I'd say. Well, then. Let's see if it actually has any results."

"Perfect! I'll go first this time!"

Qing didn't hesitate—rushed in right away.

Since her goal was to master flow and softness, defending would be pointless. She needed to move.

She swung her folded arm outward in a sweeping half-circle.

Nan-gong Shencai's sword intercepted the path—so Qing twisted her wrist, letting the flat of her blade skim against his, instead of the edge.

At the same time, she supported her wooden sword's flat with her left hand and gave it a sharp push.

"Nice!"

He shouted, and in that instant—a gap!

Qing's eyes gleamed as she launched a technique.

Yue Maiden Sword Form – 'No-Self Wandering Step'.

As lighthearted as a child playing with a monkey.

\textit{Or… wait. Is that actually lighthearted? A monkey and a kid playing sounds more like chaos—}

"Ugh—!"

At that moment, all the strength drained from Qing's body and her breath caught in her throat. The next thing she knew, her cheek was pressed against the soft training yard dust, warm grains scratching at her skin.

"H-Haaah… hu… hff… hhh… dammit…"

Qing gasped for air like her life depended on it.

If you got struck in the solar plexus with the point of a wooden sword, it didn't matter how far beyond human durability you were—you were still going to eat dirt.

"Mm, Sword Friend. It seems to me you got a little too absorbed in softness just now. If you'd followed through with the motion, it might've worked. But you ended up doing something neither here nor there."

"Ughh… Seriously, are your strikes getting more brutal lately…?"

"Stop being dramatic. You're clearly fine. Get up now, Sword Friend."

Okay, so she didn't have any broken bones or torn muscles or lingering damage.

Qing took Nan-gong Shencai's outstretched hand and stood up. Her breath had come back, but every inhale made her whole torso ache.

"Still, your first move was excellent. The transition from hard force to softness, using a push to follow through—it was what we'd call a perfect first form, nearly equivalent to a vital-stage martial move."

"Hmm. So, the training's working?"

"Who knows? We'll only see with more practice. Come now, Sword Friend. You think we've got time to stand around? Even as we speak, the sun is setting on this fleeting life."

It was still midmorning, so the whole 'sun setting' thing felt a bit dramatic, but… technically, he wasn't wrong.

Thus came a record of twenty matches, twenty losses.

A total wipeout.

However, Nan-gong Shencai's evaluation was more optimistic.

"No doubt about it now. That bizarre training method is working. I should find myself a sharp dagger too. Or, no, as a proper swordsman walking the righteous path, I should go with a longsword instead."

"I lost every match, though?"

"Only because I've reached the point where I can't go easy on you anymore."

"You're saying my swordsmanship's grown that much? Enough to keep up with you?"

"Not quite. But it has reached the point where I can't go easy on you. Your external martial power is so exceptional that, even though your swordsmanship is still lacking for your stage, I can't afford to underestimate you."

"Did you really need to say the part about it being ‘lacking'…?"

Qing grumbled, and Nan-gong Shencai smiled gently, offering his honest assessment.

"You were just forcing softness into your forms too hard, which left openings. But beyond that? The principle of flowing force is already embedded in your swings. Your stance is clearly different from yesterday's. That alone proves your training is paying off."

Even the sound of their wooden swords clashing had grown quieter—proof that she was learning to absorb strength into softness.

After that, Peng Daesan arrived with Peng Chaolei, and Qing once again took a good beating across the ground.

Still, against the two of them, her win rate did tick upward slightly, so maybe this crazy training really was working.

It was just before lunch when Qing, covered in sweat and dirt, started heading to the bathhouse to wash up.

"Tsk, tsk. What a pitiful sight you are."

"Ah! Uncle, you came again?"

Tian Youxue was back in his usual spot—this time fully reclined under the shade on a woven mat like he'd just moved in.

"So, how was the training? Rough, wasn't it?"

"Ugh, don't even start. It took me three whole shichen just to eat."

Qing groaned, exhausted, while Tian Youxue chuckled like the inappropriate old man he was.

"That's how delicate your fingers really are. You've got five on each hand for a reason. You think replacing all that with one sharp blade is supposed to be easy?"

"Definitely not…"

"Looks like you went with hemp clothes thinking they'd be easier to manage than cotton. But from the looks of that intact hem, I'd say you gave up in the end, huh? Keh keh. In that case, I might as well teach you a little trick—"

"I didn't give up. I dressed myself. With the dagger."

"Tch. Kid, don't lie to your elders."

"I'm not lying."

"Hmm? Can you swear on your master's name?"

"Sure. I ruined like five sets, but I managed to patch one together well enough."

"……"

Tian Youxue was momentarily speechless.

Because… he hadn't expected her to actually succeed.

This wasn't a technique he taught intending for her to master it.

Not only that, but hadn't he handed her the Azure Blade, a weapon infamous for its almost supernatural sharpness?

Granted, Tian Youxue could do all sorts of things with that same dagger during training.

But when he first began learning from his own master, he'd started with blades that were practically dull. The thing was so stubby and round-edged, it barely qualified as a carving knife.

Only after getting used to it did he start sharpening the edge and extending the blade.

But the Azure Blade?

That thing was leagues sharper than anything he'd ever trained with.

Back when Tian Youxue was still practicing, he hadn't even managed to steal the Azure Blade yet.

Meaning… Qing had succeeded in training with a weapon that was more advanced than anything even he had used.