\chapter{Let's Have a Spar (2)}

Certainly, Nan-gong Shencai was helpful for sword training, as after hearing that she relied on strength, Qing reviewed the martial arts she had learned and found that most of them took an aggressive approach.

Even setting aside the Yue Maiden Sword which felt like a compilation of all subtleties, the rest were like that.

Most demonic arts can only be aggressive.

The One Hundred and Eight Asura Sword based on the ferocity of beasts biting and tearing, the White Hand Demonic Arts that tear and strike enemies, and the Black Slaying Demonic Palm that shatters.

Buddha's Palm was also aggressive.

Buddhist martial arts are originally based on straight lines and destruction. It's probably because of the non-killing techniques that subdue by shattering bones and muscles without killing.

Qing thinks it would be more merciful to just kill cleanly, though.

So it was hard to grasp what softness meant, taking the force out of the body and weapon, flowing and penetrating and shaking.

There was one suitable martial art, so Qing opened her martial arts window and poured plenty of training points into Shadowless Divine Hand.

Then, as usual when learning a new martial art, she rolled her eyes back and twitched before finally coming to her senses and rubbing her eyes.

Apart from that, the applications of Shadowless Divine Hand that invaded her mind had quite interesting aspects.

This really was a thief's technique…

The operation of the martial art itself was exactly like that, with stealthiness at its core, manipulating without the opponent noticing.

Techniques like attaching sharp things like artificial nails to the index finger to secretly cut pouches, clothes, or knots.

The method of putting your hand through the hole made like that to take things out or put things in was exactly the technique a thief would use.

Why on earth does a qi technique for unlocking exist in this world?

It seemed like whoever created this martial art had truly impure intentions.

Of course, these applications just explained in great detail how to do bad things with the movements of Shadowless Divine Hand, but the movements themselves were faithful to the Golden Silk Hand that grabs, breaks, and twists.

So Qing tried to use Shadowless Divine Hand with a sword.

"Hmm? Sword Friend?"

"Hahah! How is it!"

The two wooden swords clashed with a cute tok sound.

Then Qing's wooden sword slid down along Nan-gong Shencai's wooden sword.

When Nan-gong Shencai turned his sword to guide it outwards, Qing responded and the two wooden swords remained stuck together, pushing and pulling without separating.

"My goodness, Sword Friend! They say rapid progress is surprising, but to understand this much in just one day!"

"I'm pretty amazing, right? Want to praise me more?"

Nan-gong Shencai turned his wrist to deflect Qing's wooden sword with the outer blade, then suddenly thrust straight in.

Qing aligned her feet in a straight line and stepped diagonally to the side, extending her wooden sword held straight like a wine cup to deflect the thrust outwards.

Connecting, riding, pushing, and flowing.

The two wooden swords rarely clashed, and even when they did, only cute tok tok tapping sounds rang out.

After about fifty exchanges like that, Nan-gong Shencai showed his palm and slowly stepped back.

"Whew. Soft swordsmanship is indeed a bit tiring. But, how did you become vulnerable to attacks while taking a soft approach? You're only skilled at pushing and sticking, focusing entirely on defense, so no decision can be reached."

"Hmm, yesterday you talked about softness, so I tried using Golden Silk Hand with a sword. But um. Golden Silk Hand isn't a technique for stabbing and cutting."

Golden Silk Hand was originally a technique for grabbing with the hand, binding, breaking, and pushing to knock down.

It's not even a martial art meant to be used with a sword in the first place.

So it felt like adding another joint, and while she could push or pull without damaging the wooden sword, that was all she could do.

At most she could slide along the blade to hit the opponent's fingers, but Nan-gong Shencai was so skilled he never gave her an angle.

"Hmm. Then couldn't you just apply those techniques to the sword techniques you usually use?"

"I tried to see if it would work or not. Hmm. Now I'm going to practice that kind of thing."

Just now she had used it with a sword instead of her hands, so it was an attempt to piece it together herself.

Having confirmed it worked well enough, now it was time to apply it to swordsmanship.

But, thwack!

"Ow!"

"Oh no! Are you alright!?"

"This much is nothing. My body is so sturdy that this level doesn't bother me at all."

Qing said while massaging her shoulder.

However, contrary to her words, she had properly allowed a hit for the first time in a long while.

It was a very painful defeat that would have cost her an arm if it had been a real sword.

It was because of Qing's suddenly clumsy swordsmanship.

She could try something completely new.

But it wasn't easy to twist movements that were ingrained like habits in her head and body.

Rather, Qing's will interfered, making it an ambiguous flailing that was neither here nor there, so the moment Qing moved her sword with her own will, her entire body was full of openings.

"Hmm. Strange. Sword Friend. Suddenly you don't know what to do? You're acting like someone experiencing real combat for the first time."

"Hmm. What does that mean?"

"Should I say it feels like someone who has only perfected the form of movements by swinging alone, without sparring or martial arts competitions, is using them in real combat for the first time?"

The movements Qing used took the form of martial arts in their most complete state.

It was a method of just storing in her head and using the imagery taken by the originator of the martial art, not Qing's own imagery.

However, she could use them broken down into very detailed fragments, so she did have a level of proficiency similar to a master's level of deconstructing movements.

But when she tried to modify them instead of just using them, the limitations of martial arts learned improperly were immediately exposed.

"Hmm. Sword Friend. Actually, I can memorize movements perfectly, but I can't apply them at all."

"You memorized swordsmanship and used it? It's extremely strange, but hmm. Now that you say it, I somewhat understand."

When facing Qing, Nan-gong Shencai always felt like three different swordsmen were alternating.

When using the Yue Maiden Sword, there was a childlike innocence, and when using the Divine Maiden Sword Sutra, there was a dignified determination to stand in the world like a great man.

And occasionally, there was an unnamed swordsmanship with a terribly murderous intent that tried to bite the nape of the neck without hesitation.

Since she didn't try to reveal it herself, he could only guess it was probably one of the killing sword techniques frowned upon by society.

Until now, he thought the respectable Sword Friend was accurately reading the essence of each swordsmanship and using it with the originator's imagery.

But she said she just memorized and used them, so should he say her intelligence is amazing, or that her overly excellent brain power is rather hindering the development of her skills?

Listening to what she's saying now, in the end-

"Sword Friend, you haven't improved at all in terms of skill since we went to Mount Hua two years ago?"

"Hmm, are you, disappointed?"

"To be honest, I am. In the end, you've only developed a strange habit of overpowering with physical strength and inner power, but as a swordsman, shouldn't we say you've rather regressed? How on earth have you been training all this time to end up like this?"

At this, Qing looked around sheepishly and said:

"Hmm, I'm trying to do it properly now. Um, it might not be any help to Sword Friend, but can I ask you to continue sparring with me…?"

"Is that what you're saying! Now that Sword Friend has finally stepped on the right path, I rather want to rejoice and congratulate you!"

Nan-gong Shencai showed his teeth.

Qing showed the same smile in response.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Nan-gong Shencai unpacked his luggage in one of the Wucheon Pavilion guest rooms, so it was sparring from the morning, and after lunch, the Peng siblings, Peng Daesan and Peng Chaolei, came to visit for more sparring.

There was a minor incident where Nan-gong Shencai mentioned half-swords and received a beating disguised as sparring from Peng Chaolei.

After dinner, he spent time with Tang Lan-Ah, who had been watching boredly all day.

Tang Lan-Ah wasn't going to participate in the Hidden Dragon Martial Arts Competition anyway.

'You've been poisoned with the Seven Treasure Poison, if you don't surrender within six steps, even Hua Tuo couldn't save you.'

First of all, she couldn't say such things after poisoning someone, and if she said she was going to use poison, what would be the point of the martial arts competition?

While Qing was training, she showed herself preparing poisons in her own way, throwing around hidden weapons and occasionally boiling medicinal ingredients or smearing, baking, and burning things, but you could clearly see she looked bored.

After going out to play a bit at night like that, they washed up and got into bed.

"I can't live like this! What is this!"

"Hmm. Traces of effort?"

"You should do sparring and everything in moderation! You got hit a lot today. Why didn't you just asked them to go easy, why didn't you say anything until it got to this point?"

Tang Lan-Ah burst out angrily at Qing's skin covered in bruises here and there.

"Well, going easy wouldn't be much help. And anyway, it's just bruises, it's not like bones or muscles are damaged."

"Am I the doctor or are you? Look-"

After taking Qing's pulse, Tang Lan-Ah muttered as if dumbfounded.

"-Ha. But you're fine again. What kind of body is this. Still, even if you're fine, how can a woman get hit until her body is colored like this? What kind of stupid training is this?"

"The sweat drops shed now save blood drops in the future."

"Your words flow like a mountain stream. Besides, you, did you train like this in the Divine Maiden Sect too- um. Did you train?"

Tang Lan-Ah was confused for a moment.

Come to think of it, she seemed to have said she was training while in that bizarre state in the Divine Maiden Sect.

It seems strange to criticize someone for saying they'll train hard.

"Forget it. Let's sleep."

"What's this? Something's strange…"

Tang Lan-Ah tilted her head.

There was something unsatisfying about it. What was it?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's training in the Divine Maiden Sect, mainly sparring with Ximen Surin, was always training with real combat in mind.

Thanks to this, she could use movements more skillfully than anyone else, so the focus was on properly using what she had.

And this time, the focus of the sparring was on completely melting down what she had and making it her own.

After about five days of getting hit while continuing to spar with Nan-gong Shencai, the Peng siblings, and even Gong Sun-Yaoyi joining in, the sparring that used to result in ten losses out of ten fights became one win out of ten.

There was one person clicking his tongue at this sight.

"The Godmother's disciple. She's tough. Really tough."

The Divine Thief, the man called the world's greatest thief, clicked his tongue.

The Fragrant Traces had split into two, weak and strong.

Of course, he looked for the strong side, but he came up empty-handed for the Fushen-di he was actually looking for.

However, he did discover a strange group called the Xue Family Company, which strangely had many masters and an unusual flow of money.

He investigated because it was suspicious and achieved the feat of uncovering a secret branch of the Demonic Cult. But it wasn't particularly of interest to the Divine Thief.

Originally, the fact that the Demonic Cult was planting merchant groups in Zhongyuan and taking money was a secret everyone guessed, so there wasn't much use in discovering one of them.

So he returned to Kaifeng and tracked the almost disappeared Fragrant Traces, which led to the honored guest quarters of the Wucheon Pavilion in the Wulin Alliance.

And while looking for an opportunity, he happened to witness Qing using Shadowless Divine Hand with a sword.

"That, that woman properly read the secret manual back then! She was pretending not to know all along! Huh, the great Divine Thief was completely fooled!"

It was a bit different, but not too different.

In any case, it was the same in that martial arts had been stolen.

And then, it wasn't about the Fushen-di anymore.

It was because he had found the successor that all previous Divine Thieves had found most difficult, that fated one they had been looking for.

Someone who stole the Divine Thief's things should rightfully inherit the Divine Thief's name.

So he looked into it, and oh my.

She already had a master, and it was that Godmother.

But if he gave up because of that, he wouldn't be qualified to inherit the name of the Divine Thief.

Because the Divine Thief never gives up.

So the Divine Thief thought.

\textit{Can't a great thief who can steal everything in the world steal someone else's disciple?}

\textit{Rather, if she's the named disciple of the Zenith Among Women, isn't this an opportunity to make the name of the Divine Thief famous?}, he thought.
