\chapter{Let's Have a Spar (4)}

The Yue Maiden Sword Form flowed in smooth, fluid arcs.

The blade's trajectory curved into a wide circle—then, without warning, it dropped like a calligrapher's hook stroke and whipped upward. Qing's right hand, pulled tightly across her body, snapped open as she slashed diagonally upward from left to right.

Peng Chaolei dodged, spinning gracefully as the wooden sword grazed the curve of her back, dangerously close—but ultimately just slicing through air. Her long hair fluttered outward in a soft rustle.

Qing's eyes lit up.

\textit{An opening!}

She yanked her sword back, raised her hand high—and brought the blade down with vicious precision, aiming straight for the crown of Chaolei's head.

The wooden sword sliced through the space between Chaolei's spread hair, but… it met no resistance. It felt like it cut through fog.

CRACK! Qing's world spun sideways.

Chaolei had spun her body low and swept her iron cudgel across the ground. The heavy steel rod—massive and blunt—had looped into a wide arc and smashed hard into Qing's shin, just above the ankle.

Both her feet left the ground, and she toppled sideways, landing hard on her shoulder.

"Ghh—tskk…"

Considering the fall, her groan was kind of half-assed. The blow had knocked her completely horizontal in midair, but she rolled up almost instantly, gave her calf a quick rub, rotated her shoulder, and grabbed her sword like nothing happened.

Then they clashed again.

Twenty more exchanges later, Qing took a direct hit to the thigh—just below the hip—and hissed through her teeth, massaging the spot with a grimace.

Zhuge Lixian, watching from the sidelines, winced and tried to speak up.

"Sister Peng? Maybe… a little less force?"

"How? You want me to slow down mid-swing by force? That's not how this weapon works."

Peng Chaolei wielded a giant blunt steel cudgel in place of a proper sword. Counting the grip, the thing was over six and a half feet long—solid metal.

It weighed nearly twenty jin\footnote{About 12 kg}.

You couldn't swing something like that with brute strength. You had to move with its natural rhythm, let its sheer weight carry the momentum. The whole art lay in controlling its rotations—keeping the energy flowing unless it hit something, in which case the rebound just continued the circle.

She was just holding on and steering. 'Going easy' wasn't even on the table.

"She's right, you know," Qing chimed in. "You can't call it training unless it hurts. Real growth comes with real bruises."

Classic method of Ximen Surin — that woman practically beat her lessons into you. And Qing? Qing was a believer.

Chaolei looked genuinely touched, smiling proudly.

"My sweet Qing's really growing up."

"Honestly, I just had a lot of catching up to do."

At first, Qing couldn't even last a single move. Her wooden swords broke constantly.

Trying to block a giant iron weapon with a featherweight training sword and no internal energy buffer? Yeah, no. If her deflection angle was even a little off, snap—instant sword death.

So Chaolei had started out straightforward. Pure strength, no tricks. But as Qing got better, she added finesse, then deception. Now, even with Chaolei using every skill in her arsenal, Qing was holding out through twenty-plus moves.

Sweaty and satisfied after a good spar, Chaolei finally stepped back, wiping her face with her sleeve.

Qing patted the dust off her now dirt-brown training uniform.

"Phew. Who's up next? Sword Friend?"

"Yes! I've been waiting!"

"Keep it short and get out of the way."

Now that Qing was on fire, everyone was raring to go. It was a gathering of born martial artists, after all. Even Nan-gong Shencai, who was basically always fired up, wasn't alone anymore. The Peng siblings had finally adjusted to Qing's batshit training methods.

The difference was clear.

Ten days ago, when these nonstop sparring sessions started, the sounds of Qing getting hit were modest: thwack, thump, tap.

Now? You heard KWHAM, SMACK, THUD—it was viscerally unpleasant. Zhuge Lixian, who only dropped by occasionally, had every right to be alarmed.

"Sister Tang, is this… is this really okay? Human bodies aren't meant to take this much abuse, right?"

Tang Lan-Ah, who'd been laser-focused on her throwing weapon drills, tilted her head.

"Huh? Qing? She's fine."

"She's… fine?"

"Qing's built different. She's always got her self-protection energy active, so getting hit like that doesn't even bruise her muscles, let alone break bones. If it's not sword energy or a blade, it won't even cut her. Can't give her acupuncture, either. Ugh, this one's stuck. Stop gawking and help me out."

"O-Oh. Yes, ma'am."

Zhuge Lixian quickly pulled the throwing knives out of the wooden practice dummy one by one.

Lan-Ah took them as he handed them over and casually stuffed them into her wide sleeves, her inner coat, and the long, billowy hem of her outer robe.

The flowing style of Tang Lan-Ah's outfit wasn't about fashion—it was functional. A walking armory.

Zhuge Lixian stared.

\textit{Mental note: never piss off a Tang clan martial artist.}

"And hey, isn't it kind of inspiring?" Lan-Ah continued. "Seeing her go that hard makes me want to get serious, too. Makes sense she hit late-stage advanced level already. Our Qing's something else."

Zhuge Lixian nodded.

In the end, he was a martial artist too. And martial artists… well, they had a hard time telling the difference between 'working hard' and 'wrecking yourself'.

By sunset, Qing was a mess.

Her uniform, soaked in sweat, stuck to her body as she rolled across the practice field. Dust clung to her like wet cement, caking into a paste.

"Whew…"

Today's win rate: about ten percent.

It hadn't improved much. But that wasn't because she wasn't getting stronger—it was because everyone else was taking it more seriously, ramping up the intensity.

So yeah, she was definitely growing.

She dragged her aching, exhausted body toward the baths, feeling a warm sense of accomplishment—only to be stopped cold.

-Tsk-tsk. What a fine way to train, huh?

A voice.

Qing flinched, turning her head—and spotted a short, middle-aged man leaning against a tree she could've sworn had been empty a second ago.

"Shit! You scared me. Uh, who are you? You seem kinda familiar…"

"What if I talk like this, yong? Still don't remember me?"

"Oh! The fake book peddler!"

Qing immediately recognized the weird speech pattern from that shady vendor she met in Heuksi.

Thanks to Zhuge Lixian's lecture on the Shadowless Divine Hand, Qing had a good idea who this guy actually was.

Could this be the guy who took her Fushen-di?

But if she asked directly, she'd basically be admitting she knew his identity. So for now, she played dumb.

"Name's Tian Youxue\footnote{天有學. Tian is rarely used as surname. Youxue means 'posses knowledge'. Cheon Yuhak (천유학) in the original text}. Been watching you for a few days. Damn, girl. You're intense. Totally insane."

"Me? I'm fine. But you probably shouldn't say stuff like that. If my master hears you talking shit, she'll break you into pieces."

Because this guy screamed 'suspicious', Qing casually dropped Ximen Surin's name like a trap.

"Oh yeah? And what exactly did I say that deserves a beatdown?"

"If I weren't in this body —if I'd been born a man— would you still say I'm ‘too intense'?"

When a man spends his days drenched in sweat, rolling in the dirt, taking hits and training nonstop, people say, 'What resolve! What a promising young man — he'll be a legend someday!'

But when a woman does it? Suddenly she's 'a bit much'. People click their tongues and mutter, 'So obsessed… Who on earth would take her in like that?'

That's how things are in the martial world. No wonder Ximen Surin raised hell when she was young.

"Mm… I mean, I probably still would've said you were a bit of a bonehead…"

Tian Youxue deflected, clearly hit where it hurt.

"Anyway," he said quickly, "what the hell kind of training is that, huh? From where I'm standing, it looks like you're just trying to wear yourself out. What—is the pain, the soreness, the bruises—does all that make you feel accomplished or something?"

He wasn't wrong.

Because he wasn't a full-time martial artist, he had the distance to see through the romanticized idea of 'working hard'. He could spot the trap hiding under the word 'effort'.

Qing's face soured.

Who was this guy to start giving lectures out of nowhere?

"I've actually improved a lot, okay? I used to fold in just a few moves, and now everyone's treating me seriously."

"Hmph. Improved, my ass. Even the mutt down the street would learn to dodge after getting beat that much. You didn't get better. You just got used to getting hit."

"That's still a kind of progress."

"And what, you gonna go get beat up by every fighter in the world now? See how long that lasts."

\textit{What's this guy's deal, seriously?}

The way he talked—his whole attitude—was driving her nuts.

Qing's eyebrow twitched. But she held it in. Once.

"You know, anybody can backseat train. So, what, you've got some genius training method or something?"

"Sure, anyone can backseat train. But when I see someone breaking their back for no gain, am I supposed to clap and say, ‘Good job, champ!'?"

"Well I don't see a better option, so I'll just keep doing what I'm doing. Whatever you were up to, go back to it. I'm out."

She gave a polite bow and turned to leave.

If someone's not helping, their advice is just noise.

"Hey now, hold on. You're just gonna walk away like that?"

"Of course. Was there something else?"

Tian Youxue realized he'd screwed up.

He'd let his own irritation color his words, and now he was losing her. He quickly reached out to stop her.

"You're trying to learn softness, aren't you? I could tell — you're trying to bring grace into your sword."

"…Yeah. That's right."

"Hmph. But swords aren't exactly soft by nature, are they? You could swing it ten thousand times and it still won't flow like silk. That's not how softness enters the body."

"Then how?"

"Get yourself a sharp dagger. Actually, here."

He pulled a dagger from his sleeve and tossed it in a perfect arc.

Qing caught it. Drew it.

The blade gleamed blue. It was no ordinary weapon.

"Wait, are you giving me this?"

"Lending it. For now. From this moment on, consider that dagger your hand. Use it in place of your hand."

"…What does that mean, ‘in place of my hand'?"

"Exactly what it sounds like. Eat with it. Dress with it. Do everything you normally do with your hand—but use the dagger instead. Don't let it leave your hand. Not until you go to sleep. And obviously, no cheating with your left hand."

Qing looked at the dagger with a mix of suspicion and reluctance.

But… a master-level guy probably wouldn't go out of his way to lend her something this expensive just to mess with her.

"You're not screwing with me, right?"

"Would I bother? I learned this way myself."

"…Thanks."

Qing gave him a slight bow.

Tian Youxue nodded and continued.

"By the way, don't you want your Fushen-di back? There's a note I left inside the flute—should be a handkerchief tucked in there too."

"Oh, that thing? What the hell, why'd you take someone else's stuff?"

"What do you mean that thing? You read the note—should've come to meet me, no?"

Tian Youxue looked half-offended.

Qing, meanwhile, looked completely unbothered.

"I only noticed right before bed. The meeting time had already passed. And you did write that you meant no harm, so I figured you'd reach out again."

"I mean, if someone steals a priceless heirloom from you, you're supposed to run to get it back—not act like you forgot a grocery errand!"

"Who'd even want that ugly-ass flute? Probably doesn't even make sound."

"Kid! Do you have any idea how much that thing is worth? That's pure thousand-year cold-forged iron! You could make a divine sword out of it—it's a national treasure!"

"Then why ruin a perfectly fine flute just to make a sword? Wouldn't you rather have something that makes music than something made to kill people?"

"…Gods, you sound like a monk."

She wasn't trying to be.

Qing just didn't care about material things.

Not because she was born that way, but because she lived like someone who didn't know if she'd survive tomorrow. People like that don't think about saving up. Once you've experienced the world flipping upside down, you stop imagining it'll stay still.

Once something's happened once, it doesn't feel weird when it happens again.

Tian Youxue finally got to the point.

"…So. Let me ask. Ever thought about learning a martial art? I've got a few techniques with names that echo across the land."

"Thank you."

Qing bowed.

Tian Youxue lit up like a lamp.

"Then let's start with the nine-bow disciple cere—"

"Oh, that's what you meant? Sorry. I can't serve two teachers."

Her whole attitude flipped mid-sentence.
