\chapter{Let's Have a Spar (13)}

Qing climbed the steps leading to the medicinal bath.

Looking down, she felt dizzy—it was like staring at actual lava.

She cautiously tested it with her foot and recoiled in disgust.

\textit{What the hell, why is it solid?}

"This—what is this!? It's solid!"

—You can even jump on it. Amazing, right? After jumping around a bit, if you stand still, you'll slowly sink in.

Following the voice, Qing started hopping on top of the medicine-infused bath.

The sticky sensation under her soles was gross, and she personally found stationary jumping extremely uncomfortable, so she gave up after a few bounces.

Eventually, standing on the surface of the bath, her body began to slowly sink.

Qing thrust her right arm up, giving a big thumbs-up.

Unfortunately, the water level stopped right around her navel, so the pose didn't turn out the way she'd hoped.\footnote{Terminator 2}

After struggling to lower her upper body into the resistant liquid and finally getting her butt on the submerged chair, the liquid came up just under her throat.

And the feeling of immersing her whole body in it—

"Ugh. This feels disgusting…"

—Heh, right?

It wasn't water-like at all—it was so thick and gelatinous that she could actually jump in place on top of it.

It clung to her skin like paste, sticky and slimy, like being coated in glue. It gave her the creeps and triggered a primal urge to escape.

On top of that, the smell.

With the surface level right under her nose, the sour stench was like fermented skate that had rotted to the point of chemical warfare—it drilled into her brain like a migraine.

"Gehh—what the hell did you put in this!? Urk."

—You're better off not knowing. If you knew, you'd never get in again. Just leave it at that.

That answer was worse than knowing.

What could possibly be in this for him to issue that kind of warning?

Now that she'd heard it, the bath suddenly felt even more horrific and filthy.

She imagined thousands of bugs crawling across every inch of her submerged skin.

—Gross, huh? But they say once you get used to it, it's not so bad. Or… so I've heard.

"You went in here too, right? Why are you acting like it's secondhand info?"

—Because nobody never get used to it.

"Why do you keep saying things like that…"

—This medicinal bath's official name is the Abyss of Trial Elixir. Ahem. Now, begin energy circulation. It's best to use the Awakening Sense Method. Later, if your successor has a different internal art they've already mastered, they can just circulate that. If they haven't learned the Awakening Sense Method, they should double the training time. I'll explain that part later.

"So I should circulate the Awakening Sense Method now?"

—Yes. It'll probably feel a little ticklish, but that's just the medicine being absorbed. Perfectly normal—no need to worry.

"Ah. So it wasn't just my imagination…"

Sure enough, her entire body started to itch.

It was like tiny pinpricks—almost like being gently tickled with feather tips.

At the same time, it burned like she'd rubbed chili peppers all over her skin.

And because it was happening across her whole body, just sitting still became a challenge.

But she couldn't move.

Like someone stuck in a sandpit, Qing couldn't budge.

Even with her abnormal strength, the best she could manage was the faintest twitch, painfully slow.

Still, if she forcefully exerted strength, it seemed like she might be able to escape, so she clenched her jaw and shoved her internal energy from the Awakening Sense Divine Art through her energy pathways.

Only then did the itching subside a little.

As the medicinal energy followed the flow of her internal Qi and spread through her body, her skin began to burn with such intensity that she no longer had the capacity to feel itchy.

She kept her mouth tightly shut as she circulated her Qi, but had she spoken, a strangled scream would've surely escaped.

—Hmph. Now the real suffering begins. When the body hurts, time crawls. Once the pain passes, the itching returns, and just when you think you can handle the itch, the pain hits again. For the next four hours, you'll feel like you're living through a year.

Even now, Tian Youxue refused to stop teasing.

Qing's brow twitched.

Goddamn it, she was already dying here.

It burned, froze, stung, and scorched all at once.

The worst part was that the pain wasn't that overwhelming, so it wasn't enough to blank out her mind.

She could absolutely endure it, but it picked at her nerves like someone constantly poking her, over and over.

Even the itching wasn't intense enough to make her laugh or convulse—it was just enough to make her feel like she was about to sneeze, over and over, but never did.

It wasn't unbearable because it was too much.

It was unbearable because it kept reminding her of itself—disrupting her concentration on Qi circulation and making time feel infinite.

From Qing's experience, it was like sitting through a boring four-hour lecture while nursing a mild but persistent stomachache.

And sure enough, just like Tian Youxue said, the four hours really did feel like a full damn year.

Of course it would—he'd gone through it himself and described it exactly as he remembered it.

Then—whoa, what the hell!?

"Master? What's going on? My hands—what's happening to them!?"

—What, your body's all puffed up? That's just the bath's medicinal energy flooding your system. Of course your body swelled up. Don't worry, you'll be back to normal by the end of the day.

Qing stared at her hands.

Her fingers had swelled up to twice their size, and when she touched them, they felt bloated and squishy, like waterlogged flesh.

Not just her fingers—her whole palm was swollen like a bear's paw.

Worried, she looked down—and oh god, what… what the hell was this?

If a modern Korean person had seen her right then, they'd have been reminded of a mascot from a European tire company.\footnote{Michelin}

Below the neck, she looked like that—but her face was still beautiful, which made it even more grotesque.

Thankfully, there was no mirror, so Qing didn't know.

Still, since she'd be back to normal by evening, the easygoing Qing shrugged it off and turned her attention to the state of the bath.

"Master? Is the bath supposed to look like this?"

—Heh, surprised by the rotten water? The Abyss of Trial Elixir draws in medicinal essence and pushes out toxins. Once it's done, what's left is basically sewage.

"Huh."

Qing looked down at the bath she'd just been submerged in.

The sticky, slimy mess that had reeked and assaulted her senses was now a cloudy white broth, like bone soup.

"This doesn't really look like sewage though…"

—Heh. It came out of your body, so of course it doesn't look dirty to you. Now wash thoroughly, clean your robes, and come out.

It was kind of weird, talking with a wall between them like this.

Qing rinsed her body in the clean water prepared nearby and changed into her robes.

No wonder he'd told her to bring oversized, baggy clothes.

That sneaky bastard.

Just then, Tian Youxue stepped into the bathhouse and peeked into the medicinal bath.

"Let's see, let's see—how rotten was my disciple's body—hmm? What the hell? What's with the color?"

"Did something go wrong?"

"No, it's just—when medicine is too potent, it can become poisonous. Normally, the body takes in the good and expels the excess along with internal impurities. But…"

Because Qing's body constitution rendered her immune to all poisons, she'd absorbed all the medicinal energy without expelling any of it.

So of course, nothing dirty came out.

Qing had chosen this constitution herself, and while she didn't know all the mechanics, she figured that must be it.

\textit{Yeah, that checks out.}

"Guess I didn't have any impurities."

"Hmph. What are you, some kind of reborn saint? Everyone has impurities from birth—"

"Didn't you hear? I already experienced Overhaul Rebirth. Last year."

"Ah. Right. Still weird though. Even setting impurities aside, no normal person can absorb that much medicinal energy all at once…"

Historically, not a single past Divine Thief had undergone Overhaul Rebirth before even starting formal training. So what could he say?

"Haaah. That was rough. Can we eat now?"

"You're still hungry after draining an entire medicinal bath? Food, seriously? You need to begin proper training before all that medicinal energy digests and turns into shit."

At that, Qing's expression said it all.

It was half tragic sorrow, half horrified betrayal—like, how could he say something that revolting?

"Proper training…? Then what the hell was all that just now…?"

"That was prep. The real deal is bending your joints while your body's still coated in medicine. The time has finally come to use this."

Tian Youxue dragged something out from the corner, and no matter how Qing looked at it, it resembled a torture device far more than any sort of training tool.

It looked vaguely like a punishment rack.

But with bizarre contraptions attached at every joint, there was no mistaking that this was not a normal piece of equipment.

"Uh… Master?"

"Didn't I tell you before? External body training is a combination of at least two out of four things: Overwork, torture, poison, and medicine."

Qing pointed at the contraption with one finger.

Tian Youxue chuckled as he replied.

"This one's a combo of two: Overwork and torture."

"Mm… Come to think of it, does my body really need to be that flexible if it's already strong?"

At that, Tian Youxue gave her a benevolent smile.

"I'm kidding, you fool. It just looks brutal—it's not that brutal. The training itself isn't even that hard, so no need to freak out."

"What the hell, you scared me!"

Qing sighed in relief and lay herself down into the frame.

Tian Youxue muttered something about how absurdly tall she was for a girl as he twisted, adjusted, pulled, and slotted the device into place—until finally, with several click click sounds, metal restraints locked down across her entire body.

"Master? This hurts. It's squeezing me."

"That's because your body's still bloated with medicinal energy. Once that disperses, it'll fit you perfectly."

"It really hurts though…"

"You'll be fine. At this point, that level of pain barely even registers anymore."

"…? What did you just say?"

"Now, open up. Say ‘ah.' Clenching your teeth could damage them."

Tian Youxue held out a gag.

Qing scowled and snapped back, "Master? You said this wasn't a brutal device—mmph!"

But for a divine warrior, sealing someone's mouth the moment they open it was no challenge at all.

"That was a joke too, dumbass. Can't you tell just by looking? This thing is clearly built to destroy people. Honestly, with how naïve you are, how do you plan to survive in this brutal Jianghu?"

"Mmph! Mmph—!"

"Sorry. I'm just giving you back what I got. Didn't you say it yourself? The inheritance of resentment. If it pisses you off that much, pass it down to your disciple someday."

"Mmmrrgh! Mmph…!"

"If you pass out, I'll wake you up—so don't make your master waste effort. You need to stay conscious to endure the pain; that's how the medicinal energy gathers properly."

The real essence of Flowing Flex Technique, the external flexibility training, was forcing joints to bend unnaturally while the body was still swollen with medicinal energy.

Because her body was already saturated, the joints would recover instantly as they were damaged, gradually expanding their range of motion.

But the moment those joints were forcibly bent, the pain was beyond comprehension.

It wasn't just pain—it was maiming-level agony.

And because the medicinal energy only reacted properly to that level of trauma, anesthesia or unconsciousness wasn't an option.

Under that kind of pain, no one gave a damn about masters or parents.

Qing thrashed like a wild animal, flailing all four limbs in every direction—which is exactly why this training frame had to be a custom-made steel monstrosity.

"Just hang in there for one hour. If you think of it as pain in exchange for progress, you can manage."

And with that, Tian Youxue finally dropped the mask.

Smiling wickedly, he delivered the final blow.

"For the record, I couldn't take it. I ended up bawling my eyes out, sobbing like a baby. But hey, you'll be fine. It won't kill you."