\chapter{Let's Have a Spar (10)}

Qing rubbed her head and thought to herself, \textit{Hmm… maybe I kinda deserved that one?}

Whether flicking her tongue in front of her master really crossed a line or not… well, it probably did.

But for some reason, whenever she stood in front of her master, her mouth just started running—blabbing out everything she should and shouldn't say.

"At this rate, Master's going to flatten my head… I'm gonna end up with a permanent dent!"

"Your skull is harder than ten-thousand-year iron, so there's nothing to worry about, hmm. But more importantly—did you say that so-called Divine Thief is trying to take your master's place?"

"Yeah. He's not that bad of a person, though. He even taught me a training method. But I already told him no—firmly."

Qing stepped up to defend Tian Youxue.

Honestly, it wasn't like he'd done anything for her without getting something in return.

She'd just greedily soaked up his teachings, hadn't she?

"Hmph. He tries to rope in a disciple who already has a master? That man's face must be thicker than steel. Fine. I suppose I should pay him a little visit."

"I-I could talk to him…"

"Did I say I'd talk to him? I just said I'd see his face."

"Ah. Uhh."

Qing panicked.

Sure, Tian Youxue had made a bold attempt, but it didn't work, and it wouldn't work in the future either. Now she regretted even bringing it up.

Just then—

"Qing'er! What's taking you so—oh! Hello, Ma'am. You're here?"

"Ah, it's Lan-Ah. I haven't officially arrived yet, so could you pretend you didn't see me?"

"I'll tell everyone that Qing'er had to eat separately for an important guest. I'll be on my way now."

Tang Lan-Ah suddenly appeared—and just as quickly vanished.

Among Qing's peers, she was the only one who treated Ximen Surin with such ease.

Qing, too, had realized that seeing Lan-Ah's face wouldn't help her situation in the slightest.

"Now then. Lead the way."

"Yes, ma'am…"

At this point, she could only hope the book-vendor guy—who was most likely that Divine Thief—had enough sense to run away by now.

But really, no matter how brilliant a master he might be, there was no way he could've known that Ximen Surin herself was sneaking over.

The man who'd been lying lazily on his floor mat now paused, hearing footsteps drawing near.

The heavy, dragging footfalls that used the entire sole—typical of a scrappy, casual guy—clearly belonged to Qing.

But mixed in was another sound—a soft, weightless step, like a celestial woman floating over clouds.

\textit{Did that girl forget something?}

They hadn't exactly spelled it out, but there was an unspoken understanding that this place was their little 'meeting spot'.

And now she brings a friend, without even a warning?

Tian Youxue hesitated for a moment.

But then he thought, \textit{Whatever. It's not like I did anything wrong.}

So he rose from his mat and dusted himself off to greet whoever it was.

When Qing arrived, he was no longer the lazy book-vendor scratching his belly.

Now he was Tian Youxue, putting on a composed and serious face.

"Ah, there you are, I was just about to—hmm."

Tian Youxue had started speaking in a tone of grand importance… but quickly adjusted himself when he laid eyes on Ximen Surin.

"My name is Tian Youxue, instructor of the Hanlim Academy. I have recently formed a friendship with this child. If I may be so bold, would the elegant noblewoman before me consider sharing her precious name with this humble man?"

His voice was unbearably slick.

Ugh, Qing's mouth twisted downward.

Ximen Surin, meanwhile, smiled faintly.

Tian Youxue's expression brightened—too much.

The way he looked at Ximen Surin was… unsettling. His gaze lingered with a strange softness.

Still smiling, Ximen Surin spoke.

"Hanlim Academy instructor, you say? Do you, by chance, know a certain wandering sage named Wu Sanzi? That fool who looks like a proper Taoist but is missing two front teeth—one on top and one on the bottom?"

Tian Youxue's face stiffened.

"That… that late master…?"

"Did your master never tell you the story? About how he lost those teeth?"

"Do you mean the upper ones, or the lower?"

"Did he separate the two stories? Go on then—what did he say?"

"For the upper one—he said it happened in a duel with the Shaolin Grandmaster, Monk Wunue. It was such an intense match that the monk's mercy didn't quite reach in time."

Ximen Surin's smile deepened.

"And the lower one?"

"He said it was during Qinggong practice. He was so immersed in his movement, he flew into a wall and collided with a flying egret…"

"Now that's interesting. Because I remember very clearly that I was the one who smashed it out."

Ximen Surin tapped the knuckle of her middle finger with a smug expression.

"Still the same shameless bastard. Nothing wrong with getting your tooth knocked out by someone like Monk Wunue—but to be so embarrassed about losing one to a woman that you lie to your disciple? Tsk, tsk."

Tian Youxue's expression turned grim.

"And really, colliding with an egret mid-Qinggong? What nonsense. Even the egret would laugh at that story."

"A-and the noble lady's name is…?"

"Ximen Surin. I hear you've taken quite the liking to my disciple."

Tian Youxue turned sharply toward Qing.

His face was full of betrayal.

Like a trusted minister betrayed by his emperor in one of those melodramatic imperial dramas.

Qing awkwardly looked away.

Ximen Surin still wore a smile as she spoke:

"Well? Care to explain yourself?"

"W-well, I—I am deeply, unforgivably sorry!"

Tian Youxue suddenly dropped to the floor in a deep bow.

Sure, compared to Tang Lan-Ah's ultra-graceful apologies, his was a bit clumsy.

But considering the difference in age and pride between a grown man and a teenage girl, it was a pretty decent effort.

"Of course, had I never met your disciple, I would not have dared. But once I laid eyes on her, I realized she was no ordinary child—no, she is the single most gifted talent in the entire world. And when such a gem appears, how can any teacher stand by and let her slip past?"

"So you liked her that much?"

"At her age, she has already mastered a unique Qinggong. Her senses are razor-sharp. Her learning speed shines like lightning. Could there be two such people in this world? My nature is hasty—yes—and relentless, but I couldn't help myself. I know it was wrong, and I admit it freely."

"Hmmm."

"But! Your disciple, with deep loyalty to her rightful master, rejected all offers of secret techniques and made her stance clear. I, too, gave up my intent and only wished to support her a little. I assure you, I no longer harbor ambitions of taking her as my own disciple. So please… try not to be too angry…"

"Very well."

Ximen Surin cut off Tian Youxue's explanation.

Tian Youxue cautiously raised his head and tried to read her expression.

"…When you say ‘very well,' does that mean you're forgiving me—or… uh, are you going to allow your disciple to…?"

"Have there ever been any women among the Divine Thiefs? Then one's bound to show up eventually. You've annoyed me, sure, but you are a Hanlim Academy instructor, and it seems you're not a total fool."

It was an unexpectedly generous response.

Tian Youxue blinked in surprise, completely caught off guard by the praise he hadn't dared hope for.

"Thank you! I'll become a great teacher—one worthy of the disciple of a legend!"

"Good. That's what you should do. Disciple, what are you waiting for? Are you not going to pay your respects to your junior master?"

"Um… Master."

"What? Is it so bad? I've seen enough of the Divine Thief's martial techniques to know none of them are lacking. They're all rare and exceptional. If such divine arts just fall into your lap, what's the harm in having one more teacher? Why would I stop you?"

"I'm fine. Having you as my master is enough for me. I'm not that greedy for secret techniques either…"

At that, Tian Youxue looked genuinely hurt.

Ximen Surin, meanwhile, softly patted Qing's head.

"You saying that really warms my heart. There are countless people in this world who commit unforgivable crimes out of greed for martial arts—and yet my disciple is this upright. I must have done something right in this lifetime."

"Hehehe…"

"But still, I was planning to judge the man by his character anyway. And if he's a Hanlim Academy scholar, then his knowledge alone makes him qualified to be a teacher."

Tian Youxue's expression swelled with pride again.

Qing finally got up and performed a deep formal bow.

Traditionally, you bow three times when accepting a master—once to the sect, once to your master's master, and once to your own master.

But Divine Thiefs didn't belong to any sect. And once they finished passing down their teachings, the previous Divine Thief retired and returned to whatever they were doing before.

So a single deep bow to one's master was sufficient.

Tian Youxue was all smiles.

Then suddenly, he hesitated a bit, gauging her mood, and asked—

"By the way, Senior… about my master, Wu Sanzu, and the story of how he lost his front teeth…"

"What? You want to know?"

"Yes. A disciple should know the full history of their master, shouldn't they?"

At that, Ximen Surin let out a quiet chuckle.

It was obvious from her face that she was going to use this against him later.

"It's nothing special. A scumbag tried to sneak into the Divine Maiden Sect—a sacred place forbidden to men—and had the audacity to steal a pair of undergarments. I gave him a proper beating. He ran away once he couldn't take it anymore."

The reason she'd punched him was simple:

Her personal philosophy was that all perverts should be beaten within an inch of their lives.

The Divine Thief had fled for his life.

His lightness technique was the best in the world, and he had every evasion trick—bone compression, transformation, you name it.

Even for Ximen Surin, chasing him had been no easy task.

But there was no way she could ever forgive the shameless pervert who dared invade the Divine Maiden Sect and steal her disciple's underwear.

So began a relentless pursuit.

Eventually, the former Divine Thief—cornered with nowhere else to run—snuck into Shaolin Temple for refuge.

But he'd underestimated the camaraderie between the Buddhism and Daoism sects.

In the end, Grandmaster Wunue beat the crap out of him and knocked out another tooth, and the Divine Thief was delivered to Ximen Surin trussed up like a pig.

"Are you saying my master… stole a woman's underwear?"

Tian Youxue's eyes gleamed with dangerous glee.

The look of a man who had just uncovered his master's deepest shame.

Absolutely irreverent.

Ximen Surin finished the tale with a smile.

"Turns out, the undergarments he stole from my disciple were actually a rare artifact—a Martial Treasure capable of plunging the Wulin into bloody chaos. In the end, I forgave him. If fate hadn't intervened, it never would've become such a valuable item."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tonight, Ximen Surin had decided to spend some time with her disciple.

She told the junior master to begin formal training tomorrow.

She and Qing shared a warm, intimate dinner.

After hesitating for a while, Qing spoke.

"Master… I really didn't need to take on another teacher."

Ximen Surin simply smiled.

"It's fine. No one in the world will know about it, so what's the harm?"

Ximen Surin wasn't someone to be taken lightly.

She'd done her calculations—run the numbers—and decided this was acceptable.

For one, the identity of the Divine Thief was a secret.

Which meant past, present, and future Divine Thiefs all had to keep their identities hidden from the world.

So even among master and disciple, there were rarely more than a handful in one generation.

At most: the former master, the current master, the disciple, and the disciple's disciple. Four people.

Qing would never publicly say she had two masters, and Tian Youxue couldn't exactly go around bragging, ;Ximen Surin's disciple is my disciple too'.

Of course, even if their identities were somehow revealed, it wouldn't really be a problem.

The fact that the current Divine Thief was a woman would only serve as a point of pride for all the women of Zhongyuan.

And given Qing's social position, who was going to complain?

Still, inheriting the title of Divine Thief came with responsibilities.

You had to quietly guard the martial world from the shadows—ensuring dangerous things didn't fall into dangerous hands.

Or something along those lines.

To Ximen Surin, it sounded like a noble duty.

And one that didn't even require all that much work.

And most importantly—her disciple, the future strongest under heaven, had no reason to sneak around like a thief.

She'd just go beat someone up and take what she needed.

Besides, having experienced the Divine Thief's techniques firsthand, she knew how good they were.

If Qing mastered them, all the better.

From every angle, it was a net gain.

There was no reason for Ximen Surin to oppose it.