\chapter{Let's Have a Spar (5)}

"Wait, so you just gobble up the martial arts and refuse to accept me as your master? What kind of thief—no, what kind of thieving bitch logic is that? Hm. A thieving bitch. Right, a proper thieving bitch."

Tian Youxue was so dumbfounded that it just came out of his mouth—but in fact, having the mindset of a thieving bitch wasn't a bad trait at all.

Because the successor to the Divine Thief would obviously have to be a thief.

"I was just thanking you for teaching me something, and now I'm a thieving bitch? If you don't want to teach me, fine, but why curse at me on top of that?"

"That's not cursing. If it's coming from me, it's a compliment. Anyway, don't you want it? I said it's a Divine Art! It's a martial art of unparalleled excellence!"

"I know a lot of Divine Arts too, you know? And how am I supposed to know what you're talking about if you don't even tell me its name? You gotta say the name first so I can recognize it and go, ‘Oh wow, that's a good one.'"

"You only get to know it if you say you'll learn it!"

"And how do I agree to learn it if I don't even know what it is?"

"I'm telling you, it's a Divine Art!"

"Okay, would you go buy something just because someone told you it's amazing, without even knowing what it is? You'd fork over money before even asking what you're buying?"

"Ugh, I'm dying of frustration here! It's a Divine Art! A Divine Art!"

"Yeah, and its name is…?"

Tian Youxue pounded his own chest in exasperation.

Qing's argument was rational.

But martial artists were a different breed—if someone said they had a Divine Technique for sale, they'd drop piles of gold on the spot.

That's just what Divine Techniques meant to people in the martial world.

Of course, Qing didn't count, since she fully intended to flip the deal and trade it away later if she felt like it.

"Ahem. Well, if you've got nothing else to say, I think I'll be on my way now? My body's starting to cool down."

"You're seriously not even tempted by a Divine Art?"

"I told you, I already know plenty of those. And even if I were tempted, what can I do? I already have a master. I'm not gonna go collect a bunch of them like they're inheritance sponsors. It's not like people have multiple parents just to grab more assets, right?"

"Says who?! You think there aren't people out there with more than one dad? If someone announced they'd pass on a Divine Art, you'd have enough idiots lining up to call them ‘Dad' to fill a whole city!"

"Then go find one of those people. I'm not looking to serve anyone other than my master. Thanks again for the training advice."

Qing bowed her head and trudged away with the weary shuffle of someone completely drained.

No kidding—now that the heat in her body had worn off, she was aching all over, soaked to the bone, her clothes were a muddy mess, and everything felt ten times heavier.

Tian Youxue stared blankly at her retreating figure.

"So she's got loyalty, huh. That's even better. Alright then. Let's see how this plays out."

Still, the thing about thieves was that the more precious something was, the more they burned to steal it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Use the dagger instead of your hand, was what that suspicious old man had said.

Qing didn't waste time. She tried the new training method right away—starting with dinner.

Peng Daesan's evaluation was merciless.

"Do you have some kind of grudge against the food? What exactly are you trying to do?"

"Hmm. Just following advice from some passing expert. He said to use the knife in place of my hand. And, well, it cuts a bit too well…"

Qing hadn't thought eating with a dagger would be that hard.

Including the handle, it was only about 42 centimeters long—by the units of her hometown. The blade itself was short, with a grip about the length of a typical dagger, so she figured she could just stab chunks of food and eat like that.

But the blade cut way too cleanly.

When she stabbed into a chunk of duck meat, it felt like sliding a blade into tofu.

And when she lifted her hand, the meat didn't even twitch—just glided off the dagger as if the blade had slipped out by itself.

She changed tactics, skewering the meat sideways. But the balance was off—it leaned to one side, and the smooth blade just sliced right through it, sending the meat tumbling off the side.

In her obsessive pursuit of duck meat, Qing ended up mutilating the poor thing into shredded disaster.

"Ugh, this is hard."

"Unless you plan to sit at the table all day, stop doing that ridiculous nonsense and just eat already."

"Tch. I've gotta give it a real shot first. If I run into that expert again, I at least want to say I tried. You can't just quit because something's hard. It was advice from a master in the Haegyeong realm, after all."

She carefully skewered another chunk of meat, this time lifting it while keeping the dagger upright. She let it drop against the flat of the blade—

And the meat slid down the blade, the razor-sharp edge slicing clean through the side, and flopped helplessly onto the table.

"What the hell? Why is this knife so sharp?"

"Sister, if I could see that dagger for a second… hm."

Zhuge Lixian took the dagger, examining the edge with one eye, bending it slightly to test its flexibility, then holding it up to the light like some sword expert.

Then he gave his verdict:

"Looks like the Azure Blade from the Azure-Crimson Twin Fiends set."

\textit{Ah. That tone. This setup.}

Qing counted silently in her head, full of expectation.

\textit{One, two, and—now!}

"Azure Blade!"

"Azure-Crimson Twin Fiends!"

"Azure Blade!"

Sadly, they were not of one mind.

Qing had said the wrong line, Tang Lan-Ah hadn't said anything at all, and Peng Daesan didn't even flinch. Should she punish them for botching the moment? Maybe ask the kitchen for a bowl of fish sauce as payback?

She mulled it over briefly.

"So… is it a good one?"

"To explain properly, I suppose I must first tell you about the Grand Demon Head, Tangnang Goma, from two generations ago. Ah—but to understand that tale, we should start with the Blood Massacre at Yangun Mountain Sect. Actually, no—before that, I'll have to explain how one man's careless flirting led to the whole messy chain of events that unfolded…"

"Zhuge just hasn't gotten to talk in a while and wants to go on a rant, huh? He's about to tell us all that just to explain a single dagger."

"But isn't that how it's supposed to be, Sister? You have to know the story behind a famous weapon for it to really shine."

"Meh. Alright. Might be fun."

Qing kept wrestling with the duck meat while half-listening to Zhuge Lixian's longwinded explanation.

The Azure-Crimson Twin Fiends were a paired set—a dagger and a spike-like assassin's blade—famous as the signature weapons of Tangnang Goma.

Tangnang Goma had reached the peak of demonic cultivation and might've even become the martial world's number one, if only the greatest master of that generation hadn't been none other than the Supreme Grandmaster of Wucheon.

In the end, Tangnang Goma was beheaded, and the weapons confiscated.

"I heard the Supreme Grandmaster of Wucheon kept it sealed away until its rightful owner appeared. Seems you've formed a connection with that successor."

Qing thought to herself: \textit{Rightful owner, my ass}.

Wasn't it Zhuge Lixian himself who'd told her that the Divine Thief was the greatest scoundrel under heaven?

And now, after this whole conversation—which had dragged on for what felt like three full rounds of sparring (about forty-five minutes)—she had only managed to chew through a few scraps of meat. Even that was just shredded bits with no satisfying texture. Qing was thoroughly pissed off.

"How about actually eating now? At least drink some soup or something."

"If I'm using the dagger instead of my hand, then I've got to pick up the soup bowl with this too, right? Oh. Right. I could lift it instead of stabbing things."

Qing slid the blade under a chunk of meat, gently gauged the balance, and, with an utterly serious face, slowly raised her arm.

Her body didn't just surpass human limits in strength—it did so in all aspects. That included sensitivity and balance.

Somehow managing to keep the meat balanced on the flat of the dagger, she slowly brought it above her head, tilted her head back, opened her mouth wide, and stuck out her tongue to catch it.

Peng Chaolei let out a long, deep sigh.

"Qing'er… Seriously, what kind of look is that for a lady? Don't you think it's a bit… indecent for anyone watching?"

"But it's the only way I can eat like this. And it's just us anyway. What's the big deal?"

"Well… haah. Never mind. Fine."

Peng Chaolei knew there was no point giving advice that was just going to go in one ear and out the other. She gave up early and sighed hard.

Correcting Qing's behavior? That was a feat only someone like Ximen Surin, the greatest authority on such matters, might be able to pull off.

Eventually, after forcing down a few awkward bites of meat, even Qing started to feel self-conscious with everyone watching her.

Since most had already finished eating and had nothing better to do, all eyes naturally gravitated toward the bizarre spectacle she was putting on.

Qing smacked her lips and muttered.

"Tell them to wrap this up to go. I'm gonna finish it later. I'm not stopping till I win this fight."

Peng Chaolei held back a lecture that was about to burst out of her throat.

\textit{Qing'er… who the hell picks fights with food and insists on settling it like a duel?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing, of course, brought the food back with her.

By the time she'd finally finished struggling her way through the rest of her meal, it was already late at night.

Still, cleaning her plate gave her a real sense of accomplishment—like she'd completed a serious mission.

She had literally spent from dinner till deep into the night trying to eat, and Tang Lan-Ah—who'd been bored to death the whole time and begging her to play—eventually got annoyed and went home in a huff.

\textit{Guess I'm sleeping alone tonight}, Qing thought as she began loosening her sash—then froze.

If she was supposed to use the dagger instead of her hand, that applied to getting dressed and undressed too, didn't it?

Though now that she thought about it, he never explicitly said it applied outside of meals and daily use… maybe just not while sleeping?

Qing looked down at the sash of her robes.

Hmm. Even if she helped with her left hand, was it really possible to untie this with a blade?

After a few seconds of pondering, she just gave up and shrugged off her clothes in one go, tossing them aside as she collapsed onto the bed.

\textit{I already suffered enough just trying to eat. I'll start fresh in the morning—figure out how to get dressed using the dagger then.}

She squirmed and stretched across the luxurious silk bedding of her high-end room in Wucheon Pavilion.

The soft, silky fabric wrapped around her body felt incredible. She was relaxed but not sleepy.

So plush and perfectly fluffy that she understood now why some people insisted that a proper bed was "science." It really did feel like lying on a cloud. But… yeah. Still not sleepy.

Qing lay still, eyes closed.

When sight was shut off, the other senses sharpened—and with hearing that surpassed human limits, she tuned into the sounds of the night.

But Wucheon Pavilion was top-tier, and the rooms were masterfully soundproofed. Only the faintest muted cricket chirps drifted through the sealed window. Not even a trace of human movement.

\textit{Weird. Weren't the servants staying in the farthest room on the same floor?}

\textit{Is the soundproofing really that good?}

She couldn't even hear a breath.

Then again, even with her superhuman hearing, it wasn't like she could hear someone breathing through multiple walls.

That wouldn't just be surpassing human limits—it would be ultra-surpassing them. Not even possible.

Still trying to detect any hint of life, Qing suddenly shot upright.

"What's the point of sleeping? It's not like I get tired from skipping a few nights. With my current strength, how could I fall asleep without swinging a sword at least once more?"

The words came out like an excuse—even though no one was there to hear them.

She reached out toward the nightstand next to her bed.

More specifically, toward the dagger resting on top of it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Clatter! The door burst open with a loud rattle.

Barging into a lady's room without warning—seriously, is there anything ruder in the world?

But then again, Tang Lan-Ah was a fundamentally rude woman to begin with, so this wasn't exactly out of character.

"Yah! That bitch's here again, isn't she?! Huh? What the—Qing, you're already awake?"

"‘That bitch'? Seriously?"

"Well, anytime you spend a single night away, some other bitch is sneaking in. I'm telling you, that Gong Sun-Yaoyi girl? Something shady about her."

She'd pouted and gone home yesterday, but apparently it only took one night for her mood to reset.

Qing let out a small laugh and teased her.

"You're the only shady one around here, Lan-Ah. And who said I was gone in the first place? Oh—right."

Then she added with an awkward smile.

"Hey, Lan-Ah, think you could run over to the fabric shop and buy me a bunch of cheap martial robes? Like, super thick and durable stuff. Hemp? Yeah, like hemp-linen blends."

"Huh? Hemp? Isn't that way too rough? Why the sudden need?"

"Well, because of this."

Qing lifted the shoulders of her training robes slightly.

The damage was immediately visible—sliced into dozens, maybe hundreds of threads. It looked like someone had shoved it through a shredder.

The gashes exposed patches of pale skin underneath.

Tang Lan-Ah's expression twisted into a scowl before she burst out with a sharp, furious tone.

"What the hell?! What happened to your clothes?! Who the hell did this to you?! Wait—this cliché bullshit… ah! It was that sword wench, wasn't it?! That bitch came here last night, didn't she?!"