\chapter{Let's Have a Spar (11)}

After dinner came the historic first lesson under her new master.

Traditionally, a first lesson isn't supposed to dive straight into content—it's supposed to start with a grand and elegant introduction. That's the proper etiquette of a teacher.

And so, when the Divine Thief finally spoke as a teacher for the first time, this is what he said:

"Hmph. Still, didn't I treat you decently enough? And you just go snitch on me like that? Didn't expect that from you—no loyalty at all, girl."

For an average disciple, it would've been a line loaded with pettiness that left them scrambling and flustered.

But Qing was more than qualified to be called a giant in this particular field.

Smiling sweetly with her eyes, Qing soothed the sulking adult.

"Can't we look on the bright side? It means I was loyal to my Master—and now you're my Master too, aren't you? Don't you think so\~?"

"Ahem. Even so, did you really have to butt in and say you didn't need me, when your Master had already given her permission?"

"Eeeh, but if I'd just gone, ‘Thank you very much!' right there, wouldn't that have made Master, you, and me all look shallow? I was cheering on the inside too, but sometimes, you have to play it a little cool. You agree, right?"

The Divine Thief eased up a bit.

"Ahem ahem. But you called your Master ‘Master,' and now you're calling me ‘Teacher'?"

"Isn't that better than ‘Little Master'? Would you prefer ‘Little Master'? Or maybe ‘Second Master'?"

"Can't you drop the qualifier and just call me ‘Master'? I wanted to hear that. I already have too many people calling me ‘Teacher' as it is."

"Huh? You already have that many disciples?"

"You ignoramus. Didn't you hear what your Master said? I'm a Lecturer of Instruction at the Hanlim Academy."

If the creator goddess Nüwa had sculpted Qing herself, then while she must have poured her heart into the outer form, she must've either picked the wrong material or baked it wrong—because the inside was just completely empty.

Seeing Qing's face, Tian Youxue suddenly felt a foreboding thought: \textit{Did I pick the wrong one?}

"…You don't know?"

"Am I supposed to?"

The Hanlim Academy was the greatest academic institution in all of Zhongyuan. In the past, during the Tang Dynasty when it was first founded, it had even taken on the role of educating the Son of Heaven. It had once wielded enormous influence, overseeing everything from inspections to administration and the law.

Now, after the imperial dynasty had changed hands and the people with it, it served as the heart of academia in Zhongyuan, focused on education, publishing, and scholarly research.

If we were to compare it to Qing's hometown system, the Hanlim Scholar would be the principal, and there were two assistant principals: the Scholar of Study and the Scholar of Instruction.

As the name implies, the Scholar of Study led research fields, and the Scholar of Instruction led education.

Hadn't someone said that just being a Scholar of Instruction at Hanlim Academy was enough to be called a giant of knowledge?

And yet that giant was moonlighting as a Divine Thief. It was, frankly, absurd.

"Wow. So Master's like… super amazing? Are you, like, a Grandmaster? A True Master? A Divine Master?"

Even if Qing's head was empty, her appearance was undeniably pretty—so in the face of her cute flattery, the old man's heart began to melt.

"Hmph, well, let's set the chit-chat aside for now. First of all—Divine Mas… no, wait. You little brat, you knew who I was and pretended you didn't? How'd you figure it out?"

"Uh… you showed me the secret manual of Shadowless Divine Hand?"

"Ha! So you did recognize it!"

"I never said I didn't. But seriously, why would you make a secret manual look like an erotic book? And not even a well-drawn one."

"Not well drawn?! That is the greatest masterpiece in the history of art, each page personally illustrated by Master Painter Jin Zhaoxian, the Immortal of the Brush!"

"Even if you say that, it's still just a smut book…"

"Ahem."

Tian Youxue cleared his throat, suddenly embarrassed.

"When a Divine Thief chooses a successor, the most important quality is sharp perception. The world's finest erotic book—if you can look at it without getting flustered, and instead use your eyes to discern the microscopic engravings or feel them with your fingers, then you have the sensitivity we're looking for."

"Ah. So that's what it was about."

Qing had only touched it by accident and got registered, so she had no idea it had that kind of significance.

If Tian Youxue had known, he would've thrown himself to the floor in despair.

"Ahem. Maybe I should rewrite the manual into the Tao Te Ching\footnote{Cinese classic text and foundational work work of Taoism, attributed to Laozi} or something."

Tian Youxue mused to himself. \textit{Having a female disciple makes it hard to joke about these things together…} he thought.

Of course, he severely underestimated Qing.

"I don't know who that Immortal of the Brush guy is, but for an erotic book, the art style was way too restrained. You need something a bit more primal to get that erotic pull. You're not hanging it on a wall, after all."

"Hm?"

"Like, a little more like this? Hmm… not quite getting it…"

Qing drew on the ground with her Blue Porcelain Sword.

One of the sharpest legendary swords ever known, scraping across a stone-strewn floor—it was a sacrilegious act that would've made any observer scream and slap her across the face.

But to Qing, who thought of weapons as consumables, and to the Divine Thief, who viewed treasures like mere rocks, neither of them felt anything about it.

"Hm? This kind of style? I mean, it's terribly drawn, but still… the lines… Oh. Isn't that a bit too bold? The human body doesn't really look like that."

"Come on, it's just a drawing. You can exaggerate a little."

"…? What kind of bizarre logic is that?"

In Qing's hometown, they had a device called a camera, so artists often used 'it's just art' as an excuse for anything. But in Zhongyuan, no such thing existed, so of course Tian Youxue couldn't understand.

"Still, hmm… there's something to it. I think you should learn to draw properly. It'd be nice to see what you could make."

"Eeeh, what kind of martial artist learns to draw?"

"It was the Senior's instruction. Said I should teach you the Shiyi \footnote{lit. 'Four Arts'}. You're already decent at music, and your calligraphy is said to be world-class. So once you learn Go and painting, you'll be complete. Speaking of which, let's see that handwriting of yours. Let's see why they call you a calligraphy genius."

He pulled out paper, a brush, and ink from his robe.

Qing obediently wrote four characters: First Under Heaven, My Master Is Supreme.

Her handwriting had been refined through correction until it looked exactly like the modern standard typeface of the Korean people.

Each stroke was thick yet never clumsy, soft yet assertive, and gracefully extended without any wasted space between characters. The spacing was perfect, the proportions balanced. To the people of Zhongyuan, it was a mind-blowing beauty never seen before in their world.

"My god. Every stroke settles into place like it weighs a thousand pounds. Your brush technique has already perfected an entire style—you've reached the level of a true master, no, a grandmaster! The spirit is majestic, and the grandeur rivals Mount Tai! This is the heaviest writing in all the world! How have you not made a name for yourself in calligraphy with handwriting like this?!"

He was so shocked that his normally dignified Scholar of Instruction voice burst out.

But very few people had ever seen Qing's handwriting—and most martial artists didn't get moved by penmanship the way scholars did.

In the end, the lesson went out the window as the two of them chatted and played around.

Both teacher and student were having so much fun that it wasn't a problem at all.

And so, the main topic the Divine Thief originally intended to cover finally came up only at the very end of the night.

"The Divine Thief isn't just a thief. He's a thief who benefits the world. Whether it's playing the noble outlaw or feeding selfish desires, the Divine Thief's duty is to remove harmful objects from this world."

"Harmful objects?"

"Right. When I say ‘harmful objects,' of course I mean things that are harmful to the world. Cursed demonic swords, demonic martial arts, or maybe some horrific deadly poison, for example."

"Wow, there really are demonic swords? Then do they, like, talk and stuff?"

"…? What kind of bizarre nonsense is that? Hmm. Although… I guess it's not entirely wrong, either."

There were weapons that had seduced people—swords that had drunk human blood for too long, or that had been born of deep, festering resentment, or forged through human sacrifice.

Once you grabbed one, you couldn't hold back the urge to cut people. That's why they were said to "whisper" to the wielder.

"I haven't personally held a demonic sword, so I wouldn't know. Anyway, another category of harmful items would be famous treasures. These kinds of treasures fan the flames of human greed, and before you know it, blood is spilled by someone blinded by desire."

"…So basically, steal anything that looks valuable?"

"That's what makes it the work of a true thief of the world. But if the world finds peace because of it, then isn't it worth it for one person to be called a thief?"

Tian Youxue was someone who had accumulated good karma.

If someone burdened with evil karma had said this, it would've sounded like total bullshit, worthy of ridicule. But coming from someone with good karma, it had a strange ring of truth to it.

Besides, hadn't she witnessed firsthand how he ruined his karma by aggressively pushing books for sale?

If that's how he had been squandering his karma, then perhaps he once possessed a vast amount of it.

"This is the duty you'll inherit going forward. What you steal, you deal with however you want. You can burn it, bury it, or find it a fitting owner. I used to melt down gold and turn it into ingots."

"So basically, steal all the good stuff and do whatever you want with it. Not stealing sounds like a loss."

"And don't forget to find the most talented successor and pass it all down. Honestly, that part is even more important. Treasures can be stolen again anytime—but if the Divine Thief's legacy dies out, that's the real problem."

"Got it. Raise the greatest disciple."

At that, the Divine Thief gave a satisfied nod.

"There are four martial arts that the Divine Thief passes down…"

The Shadowless Divine Hand — sleight-of-hand techniques used for stealing and pickpocketing.

Strike-Step Flash Movement — a peerless lightness skill boasting top speed in close-range combat, utterly silent.

Flowing Flex Technique — an external body art that vastly increases joint flexibility.

And finally, an internal energy method, though you only need to memorize it. There's no need to actually learn it.

Most Divine Thiefs dabbled in other jobs, so having at least one internal technique was standard.

"Come to think of it, your Master said you could handle learning multiple internal methods at once. She said you inherited the legacy of Jiutian Xiannu?"

"Yes, that's what they said."

"Of course. Jiutian Xiannu was the embodiment of Golden Mean and the Harmonizer of the Nine Realms—truly a divine figure in the martial arts world. It'd be no exaggeration to call it the greatest technique among all martial arts."

This was one of the stories Qing had pre-arranged with Ximen Surin.

It was her excuse, in case someone ever caught her using multiple types of internal energy.

Until now, Qing hadn't been sure whether it would work—but now that it did, she thought, \textit{Of course it worked. Master always has a plan}.

"Well, that's perfect. Then you're good to learn the Awakening Sense Divine Art. It's an internal method tailor-made for the Divine Thief. Originally, if no suitable disciple was found, we were supposed to adopt a child and teach it to them."

Qing subtly searched through her internal martial arts list, but oddly, there wasn't a single purple-grade technique.

Shadowless Divine Hand—gold.

Strike-Step Flash Movement—gold.

Flowing Flex Technique—gold.

Awakening Sense Divine Art—gold.

They were all golden.

Qing felt a little disappointed.

The Shaolin guys, every time she heard something about them and searched it, it was always purple. Not once was it anything less.

But of course, Shaolin boasted that all martial arts originated with them, calling themselves the true origin of all martial disciplines—so naturally, their stuff was ranked like that.

"Alright. From now on, it's yours."

Tian Youxue handed her the martial manuals.

As soon as Qing touched them, her martial window flashed a notification—it was flawless martial content.

"Starting tomorrow, I'll begin proper instruction. For today, just skim through it all and get the general idea into your head. Just assume you're not sleeping tonight. That's how real studying is done. Heh heh."

Tian Youxue's chuckle was impure.

It was the kind of laugh that said: Prepare to suffer.

But to Qing, it would take only a moment.

If she rolled her eyes back and made that nasty throat-scraping noise from the aftermath, even that would only take about one quarter of an hour.
