\chapter{Let's Have a Spar (14)}

The tensile strength of steel per unit area, even accounting for the primitive metallurgy of Zhongyuan, ranged somewhere between twenty and sixty jin.

That said, steel with strength close to sixty jin was something even iron artisans only managed to produce once in a blue moon—when that happened, they simply thanked the heavens and had no idea how it was even made.

What was considered high-grade steel typically clocked in at around forty jin.

So reverse-calculating from the unit area of the steel restraints locked onto just one of Qing's finger joints, it would take roughly ninety jin of force to break it.

But the real problem was that this contraption was designed to forcibly bend joints in the opposite direction, meaning that every joint on her body had one of these restraints clamped both above and below.

Just for the arm alone—restraints were fastened at every finger joint, above the palm, on the back of the hand, at the wrist, center of the forearm, below and above the elbow, center of the upper arm, then finally just beneath the shoulder, wrapping around like a backpack harness.

Qing had once lifted a 250-jin iron ball with a single hand and no momentum, which was monstrous strength no ordinary human could match—but it still wasn't nearly enough to break free from these bindings.

What's worse, the device was pressed so tightly against her bloated body that even assuming a proper stance to exert force was impossible.

\textit{Ah. So brute strength won't cut it.}

Qing deeply regretted her decision.

She had gone into this carelessly, thinking if it got bad she could just snap her way out of it.

Now, with strength failing her, she was learning the hard way to never underestimate a restraint device wrapped in full-body steel.

Not that there was likely another full-body steel binding system like this anywhere else in Zhongyuan, but still.

That said, the device started groaning with loud clanks and creaks—far from normal sounds.

Even if the restraints could take the pressure, the joints of the apparatus—meticulously engineered to bend outward—were clearly starting to strain.

At this rate, Qing was going to turn into a hulking steel-bound monster, like some creature from her hometown's foreign tire commercials.

Startled, Tian Youxue rushed to stop her.

"Hey now, girl, joke's a joke, but what kind of woman packs enough strength to slap Xiang Yu across the face and knock out all his teeth?"

At that, Qing paused and blinked.

Tian Youxue unfastened her gag and reeled back, repulsed by the thick string of spit that clung to it from all her thrashing and foaming at the mouth.

"Wait—doesn't that hurt?"

"It hurts. It hurts like hell. I've passed out and woken up multiple times doing this."

"Mmm… Do we really have to go through with it then?"

"Haaah. Listen. Divine Thiefs aren't some cheerful martial sects who laugh their way through cultivation and eventually reach enlightenment."

Despite the fancy title of 'lineage of one', the truth was that they were essentially an endangered species, always on the brink of extinction.

Ordinary martial sects took in multiple talented disciples, built on existing foundations, made improvements or stole new techniques, and gradually developed their martial styles over time.

But what about a lineage of one?

Without a worthy successor, there's no progress—only slow decay and decline.

And on top of that, Divine Thief moonlighted as guardians of world peace.

With their own real jobs, they barely had time for peacekeeping, let alone innovate their martial arts.

"So what's your point?"

"My point is that our training ends up like this. Call it cheating, maybe. We use swords in place of hands, soak ourselves in gold-melting medicinal baths, and dislocate joints. There's another hell-bath beyond the Abyss of Trial Elixir made specifically for the Awakening Sense Method. I'm also working on assembling your shoes for training in Strike-Step Flash Movement."

The righteous path always took time.

But when time ran out, you had to take shortcuts.

If you wanted to go quickly and righteously, you had to pay the price in pain.

If you wanted to go quickly the wrong way, you make someone else pay for it. That's why people called it demonic cultivation, or dark arts.

"…Still, this kind of pain is a bit…"

"Well. From what I've seen, you're dying to speed up your progress. Isn't that right?"

"I mean… yes, but…"

Qing couldn't deny it.

The reason she'd been dragging herself around like this lately was her own sense of urgency.

Whether it was the next crisis, a twist of fate, or some cycle in this game-like world, she couldn't shake the feeling that something inevitable was coming.

"And you think you're the only one suffering? Do you know how hard this is for me? You think it's just about pulling out some tears and snot for show?"

Sure, he joked about 'passing down the resentment'.

But the reality was this training demanded surgical precision—bending joints, tendons, and muscles exactly to their limit with absolute control.

If the force was too weak, it just hurt with no benefit.

Too strong, and it wasn't training anymore—it was an injury that would take weeks to heal.

It required the transcendent sensory perception of a Divine Thief, plus full concentration and care.

"And after all that, here I am, drained from doing Qi Daoyin for you, and you're whining. If you don't want to do it, fine. I'll just chalk up that golden three-gwan-grade bath to a total waste. Tsk, tsk."

Clearly offended, Tian Youxue grumbled as he started unfastening the restraints.

Qing glanced around, guilt etched all over her face.

"S-sorry… It's just—I get really scared of pain…"

"Is there anyone who isn't scared of pain? When others train external arts, they suffer twenty years of steady pain. You're cramming all that into about one year. That's why it's so intense. If you really can't do it, then fine. You could always stretch your joints with ointment for twenty years instead."

"No, it's okay! I'll take the fast route!"

"Hmph. Like you're the only one suffering? You think I enjoy this? I'd rather be lounging around teaching you breathing techniques and wandering about. You think it's fun for me to hear my disciple scream in agony? Huh?"

Qing looked even more apologetic now.

"I—I'm sorry…"

"Enough. The medicinal energy is good for your body anyway. In a week or so the swelling will go down. Maybe we'll move on to Qinggong next."

"Hehehe. Master, I just didn't understand before. I know you're doing all this for my sake. So please—let's go with what you originally planned, okay?"

"Hmph. You only pull that cutesy smile when it suits you. Such a conveniently timed little charm, eh? Tsk, tsk."

Tian Youxue muttered as he click click locked the restraints back into place.

Seeing that, Qing relaxed.

And Tian Youxue smirked quietly to himself.

\textit{Seriously. So naïve.}

A Divine Thief is still a damn thief.

And a good thief knows how to con people expertly.

"Alright. Say ‘ah.'"

"Ah—"

The gag was shoved back into Qing's mouth.

Tian Youxue put on a fake serious expression.

"Now shut your eyes tight—really tight. Not that you have to, but if you don't, and a blood vessel pops, you might end up crying blood. Literally."

Qing immediately squeezed her eyes shut.

Not that it helped. He just had to say something horrifying every single time—

"MMMPH!! MMFFFMMM!!!"

Suddenly, her elbow bent outward. The scream erupted from her throat by sheer instinct.

It was a pain that couldn't possibly exist in this world.

\textit{My arm, my arm! It's breaking—my arm is—}

No, really—something inside her body snapped with a sickening crack as the device forced the joint outward.

And right then, all the strength drained from her like a lie undone.

Qing's head, which she hadn't even realized she'd lifted in agony, dropped limply onto the headrest.

Three hours later.

Qing's body returned more or less to its normal shape—except now, her waist and limbs were gaunt and thin.

The rest of her body had always been well above average—not just by Zhongyuan standards, but by the standards of any people under the sky.

She looked absolutely wrecked.

Her hair was tangled like a bird's nest. Her eyes were unfocused, pupils dilated. Her tear-swollen eyelids made it look like she'd been crying for days.

Snot ran freely from her nose, bubbling at the edges.

The moment the gag was removed, a torrent of drool poured down in a stream. Even her usually soft lips were cracked and pale, with skin peeling around the edges.

"You—you said one hour…" hic.

Qing hiccupped mid-sob as she complained weakly.

Tian Youxue replied, utterly exhausted himself.

"You did scarf down the full medicinal power of the Abyss of Trial Elixir. You think we could stop halfway with all that still in your system? Still, we crammed in three sessions' worth at once, so you actually saved time. Ugh. I can't even stand anymore…"

As he said it, Tian Youxue collapsed onto the floor of the bathhouse with a thud.

Honestly, he looked like he'd just climbed out of a lake—his entire robe was soaked in sweat.

"Normally it's once every five days for ten months—so around sixty sessions. But since you inhaled the whole bath and did three times the work, we're down to twenty sessions. Even with more rest between, we can probably finish Flowing Flex Technique in half a year."

"We still have to do twenty more of these…?"

"You choose. Lower the dosage and do one hour each, fifty-seven more times. Or keep going like this, three hours each, nineteen more sessions."

"Can't we just raise the dosage and do ten total—"

"Nope. Your joints are already wrecked. Adding more medicine won't help—you still need to rest. Normally, we'd train in order: extremities, lower body, upper body. But you did it all in one go."

"Please stop saying wrecked…"

Qing mumbled without any strength.

If not for Great Tranquil Zen Art, she might've really snapped.

That supreme Buddhist internal art had been the only thing keeping her sanity afloat during the worst of the pain.

After the first hour, even Tian Youxue looked visibly aged.

Seeing him just as drained as she was made it impossible to blame him.

He'd done all of it for her—how could she be angry?

With no one else to hate and nothing left to fight, Qing could only sob, full of pain and sadness.

She remembered how Tian Youxue once said he had cried too.

And realizing that, she figured there was no point holding back.

A single tear ran down the side of her face.

She didn't even have the energy to cry properly—it was the kind of quiet, collapsing grief where your body does nothing but leak.

"Aaagh… I'm seriously gonna die. Qi Daoyin, three full hours…God, my whole body…"

Tian Youxue, completely fried, groaned to himself and then, before long—started snoring.

Loudly. Violently.

It was the kind of snoring that echoed through the bathhouse like thunder.

And everyone knows: the louder the snore, the deeper the exhaustion.

"…Master? If you're gonna sleep, can you at least unlock me first…"

Qing tried to raise her voice, but her throat was raw.

Even yelling just came out as a dry rasp, too faint to be heard over the snoring.

"Ah…"

Qing gave up and let her head fall forward with a dull thud.