\chapter{Let's Have a Spar (3)}

If you're going to steal, you have to actually do it. That's the true mark of a Divine Thief.

But how the hell do you steal someone's disciple?

Sure, you could do it physically. Kidnap them, drag them off to some remote cave halfway up a sheer cliff in some godforsaken mountain, and lock them in so they can't escape. Then grin like a maniac and go, 'Heehee, you're not leaving till you've learned everything.'

But there were problems with that method.

First, your target has to be someone you can actually kidnap. But this kid was already at the level where her lightness skill was perfect. There's no realistic way to stop her from escaping.

Second, if it were a guy, maybe you could get away with it. Sooner or later, he'd probably open his heart and fall for the whole 'Divine Thief legacy' thing. But with a girl? One wrong move, and congratulations — you've just gone from Divine Thief to Sex Pest of the Martial World.

Sure, you might pass on some martial arts that way. But the Divine Thief legacy that's been passed down for generations? That'd end right then and there.

Which means, what you're stealing isn't the disciple's body—it's their heart.

You had to win over this kid's heart so she'd willingly serve two masters.

Even the previous Divine Thief, now some revered elder of a famous sect, pretended to have that past. Acting all dignified and aloof.

Being a Divine Thief isn't a full-time job — it's a side hustle.

So, the current Divine Thief thought back to how he had been lured in by his own master.

What was it they'd said back then?

'Hey, kid, how about becoming the greatest in the world—'

'I'll do it! I'll do it!'

'Hmm-hmm, listen to the rest firs—'

'I already know! You're gonna teach me martial arts!'

Given where he came from, as soon as he heard the words 'martial arts', he'd followed that sword-wielding Taoist like a puppy.

In hindsight, it hadn't helped him at all.

Hmm…

So how was he supposed to lure this one in?

The Divine Thief blinked slowly, deep in thought.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

May 15th.

Ten days before the Grand Martial Tournament, the preliminary rounds of the Hidden Dragon Sparring Event began.

Of course, this had absolutely nothing to do with Qing.

That's because the truly elite—the ones whose skills had already been proven—didn't have to bother with the preliminaries. They went straight to the main event.

The prelims were just for disciples of minor sects or young unknowns, all fighting tooth and nail for a handful of spots in the finals.

Anyone from the Nine Great Sects or Ten Major Clans started in the finals by default. Then there were the ones handpicked by the Wulin Alliance itself as 'exempt' from the preliminaries.

Honestly? It was all about connections.

Still, no one really needed to sigh and mutter, 'God, the Wulin Alliance is rotten to the core'.

Even for the prelim participants, this setup wasn't so bad.

After all, imagine stepping onto the ring all fired up, determined to make a name for yourself, only to see a Shaolin disciple standing across from you. Wouldn't that be just the saddest, most bullshit moment of your life?

Better to just face other small fries and still have a chance at earning a flashy nickname—something cool to brag about, even if you didn't win it all.

And as for the elite already seeded in the finals? They liked this system too.

They got to scout out potential threats ahead of time. That way, they wouldn't get caught off guard and humiliated by some dark horse rookie.

Like what was happening right now.

"They say he's using the rare Earth-Crawling Fist."

"Earth-Crawling Fist? The one where you fight on the ground? You mean that, Zhuge?"

In response to Qing's official request for commentary, Zhuge Lixian eagerly jumped in.

"Ah, Sister! The Earth-Crawling Fist—yes, let me explain! But first, we need to talk about the fundamental nature of martial arts itself…"

Martial arts, fundamentally, begin with footwork. The shift in weight starts from the soles of your feet, and that momentum travels all the way to the tip of your weapon, exploding in destructive force.

That's why martial arts are generally performed standing up. Upright combat. Vertical base.

So when a martial artist gets knocked down, the standard response is either: get up immediately, or roll away to gain distance, then get up.

But the Earth-Crawling Fist, and arts like it, start from the ground. They're horizontal by design. Floor-based martial arts, so to speak.

Martial arts were made for fighting people—not attacking folks already on the ground. That's why, across every martial style, there are barely any moves designed to target a grounded opponent.

Add to that the fact that the Earth-Crawling Fist keeps the user's center of gravity glued to the floor, striking at targets below the waist—it's a pain in the ass to defend against.

"So that makes it super powerful, right? My master never taught me anything like that. Just said, ‘If someone fights you lying down, don't get caught off guard.'"

"Mm. Thing is, hardly anyone learns it. It doesn't look good, you know? And appearances are everything in Wulin. Roll around on the ground a few times and people start calling you a damn donkey. That's why Earth-Crawling Fist has another name: Dog Fist."

Yeah. That dog. The bark bark kind.

Dog Fist. As in, a martial art only fit for a mutt.

"Hmph. When it's life or death, who gives a shit about appearances? Everyone talks big, but they roll around just fine when it matters. Ooh—what's the betting line on this? Four-point-seven for Young Master Ma? Gimme a silver tael on Ma."

A betting slip vendor just happened to walk by, and Qing—smooth as ever—snatched up a ticket.

Victory slips were a kind of legalized gambling, where you bet on a winner and got paid out based on the odds.

Ancient, primitive, and thoroughly lawless Zhongyuan didn't have any rules against gambling, so merchant guilds bid for the rights to run these official betting rings before every major tournament.

Qing took her slip and eyed it curiously.

"Four-point-seven odds? Sounds like they don't expect him to win. But this Earth-Crawling thing—it's dangerous, right?"

Peng Daesan snorted.

"I said it was dangerous, not powerful. And those are crap odds. You still bet on him?"

"The long shots are the real odds, y'know? It's a fifty-fifty fight either way. If I win, I make over three silver. If I lose, I lose one. So not betting is actually the losing move."

"…How the hell is that fifty-fif—"

"Oh, it's starting."

Peng Daesan was about to argue, but the loud clang of the opening gong cut him off.

The match was on: Young Master Ma, user of Earth-Crawling Fist, versus a disciple of Huotian\footnote{lit. 'fire sky'} Gate, Young Master Cheng.

Surprisingly, Ma's use of Earth-Crawling Fist didn't look that pathetic.

He used unorthodox kicks rarely seen in most martial arts. Launching into the air, he snapped his legs together in a dynamic mid-air strike—a pretty damn impressive flying kick.

It slammed into Cheng's chest, making him stumble, and Ma used the momentum to roll into a grounded landing. From there, he spun like a windmill, pushing himself up with his hands and chaining his kicks together.

\textit{Ooh. B-boying? Kid knows how to have fun.}

Qing caught herself slipping into her hometown slang as she admired the performance.

"Huh. That's actually kinda cool."

"That? Cool?"

"Looks cool to me… Ohh, oh damn."

Qing's eyes sparkled as she watched Young Master Ma's routine—no, his martial display.

To someone like her, with a modern mindset, it actually looked stylish. It reminded her of breakdancing and the groundwork techniques in modern MMA. Nothing strange about it at all.

"You've never seen it fully unleashed."

"What? It's not bad so fa—mm."

Suddenly, Ma's style changed.

He dropped flat to the ground, stomach nearly kissing the floor, arms and legs flailing in every direction. The movements were bizarre—unnaturally fast, and deeply, deeply weird.

He scuttled around like an overcaffeinated lizard, flipped into a spider-like pose, and attacked Seong's shins and calves with fluid, unpredictable strikes. He spun, kicked, tripped, punched—arms and legs moving so seamlessly it was hard to tell which was which.

Honestly?

It looked kinda gross.

"…Okay. That's… yeah."

"Told you so."

Peng Daesan let out a smug little huff. All around them, the crowd had either burst into laughter or was snickering with thinly veiled mockery.

Especially when Ma pressed his back to the ground and started sliding forward, windmilling his arms like some kind of possessed insect.

It was a once-in-a-lifetime spectacle—one you hoped you'd never see again.

And finally, the match ended.

Young Master Cheng, humiliated by the bizarre display, slunk off with tears streaming down his face, unable to even lift his head.

Ma, meanwhile, though technically the victor, was drowning in ridicule.

In the end, even victory had its price.

And so, the true winner of the day was Ximen Qing, who turned a single silver tael into four taels and seventy copper coins.

The final victor offered her thoughts.

"But you know, even I don't think I'd win against that. Sure, in a real fight, I'd blast him to hell in one hit."

When someone's glued to the ground like that, one clean strike with Heaven-Dominating Demonic Step could rupture their organs instantly.

But in a sparring match, where you're not supposed to seriously hurt your opponent? There's just no good way to deal with it.

"It might look complicated at first, but he's basically just targeting the legs. Going for sweeps or the backs of the knees. If you're aware of that, he's not really someone to be scared of."

"You're right, Sister. A lot of those weird movements are just meant to distract. If you see through what's real and what's fake, someone at your level wouldn't have trouble at all."

Qing scratched her cheek awkwardly.

"Yeah, uh. About that. That's kind of my weak spot."

"Weak spot?"

"Oh come on, do I have to explain? If someone gets under me like that, I can't see a damn thing, okay?"

Peng Daesan and Zhuge Lixian both froze mid-blink, their eyes locking onto the same spot, before hastily pretending to admire the distant, non-existent mountains like it was the most fascinating scenery in the world.

Qing's blind spot below her feet was… significantly wider than average.

"Well, good thing I saw it in advance. If I'd gone in blind, I probably would've lost without even knowing what hit me. Worth the trip. Are there any other matches I should check out?"

"I heard there are a few martial artists using strange weapons—chairs, abacuses, iron pens. Could be worth a look."

"Chairs? Like, the ones you sit on?"

"Exactly. That kind of chair."

"…Hard to picture."

The kind of chair Qing imagined was one of those modern folding types—something you'd smack someone with in a spectacular overhead swing. Which hadn't been invented yet in Zhongyuan.

"Sister, even if they're ‘unorthodox weapons,' they're not some magical thing. It's just unfamiliarity that makes them tricky. If they were really that strong, they'd already be mainstream, wouldn't they?"

"True. There's a reason everyone uses swords."

There really was a reason swords were the standard. Outside of a few large weapons that didn't catch on due to interference from the authorities—like halberds and crescent blades—most 'weird' weapons were just that: weird.

So Qing returned to the Wucheon Pavilion, spent the rest of the day sparring, and ended her evening feeling thoroughly productive.

That's when she realized something very important.

Fushen-di was gone.

In its place, tucked into her sash, was a lacquered wooden flute she didn't recognize. She pulled on the protruding edge, and a folded note slipped out from the thin cloth wrapping it.

\begin{quote}
I'll be holding onto Fushen-di for a while.

I'll be waiting at Yuhui Inn at around Youshi.

I ask that you come alone, if possible.

I mean no harm. But if you're concerned, feel free to tell someone else where you're going and why."
\end{quote}

"…Huh. Just now noticing this."

Youshi (Rooster Hour)—that'd be around 6 p.m.

Right now? It was the end of Haishi (Pig Hour)—11 p.m.—just about time for bed.

Qing hadn't noticed the switch because she didn't use Fushen-di that day. She'd just worn it like a fancy accessory, tucked casually at her side.

It wasn't until she was getting ready for bed that she'd gone to take it off… and found a wooden flute instead.

So… what now?

Should she go, even if it was this late?

The note had said there was no ill intent. Maybe they'd contact her again later, set up another meeting.

"Miss Ximen? Is something wrong?"

Gong Sun-Yaoyi, who'd spent the entire evening sparring with her, called out.

Qing stared at the flute, then let out a breath.

\textit{Well, it's already out of my hands. No point pacing or worrying over it now.}

\textit{If they really want something, they'll reach out again.}

For now, she brushed the concern aside and flashed her usual grin.

"Nah. Just feelin' it, you know? Worked my ass off training today, and now sleep's hittin' me hard. Let's all hit the hay."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

For the record, the Divine Thief waited all night.

Just in case Qing might slip away from prying eyes and show up after dark—he waited until the sky began to lighten again.

And waited.

And waited.