\chapter{Let's Have a Spar (15)}

Qing opened the door to her room at the Martial Celestial Pavilion, exhausted, only to find Dang Nana popping up in front of her, hands under her chin.

“Tada! A bouquet for Qing'er!”

Qing just stared blankly at her with a tired expression.

Tang Lan'ah, a little embarrassed and disappointed that she wasn't getting a reaction, was about to complain when she noticed Qing's face and immediately raised her voice.

“Qing'er!? What happened to your face!? Did you cry!?”

Her face was swollen from being tortured but now it was even more puffy from crying so much.

Qing replied wearily, “It's nothing like that…”

“And what's with your voice!?”

Her voice was completely hoarse, making a whooshing sound similar to air escaping.

“It's nothing. But, where is Master…?”

“She said she was going to catch up with his friends today?”

It was understandable. Her master must have friends, and they would probably meet up on occasions like this, during the martial arts tournament. No wonder Tang Lan'ah was here. Her master was absent, so she took the opportunity to visit.

Anyway, Tang Lan'ah chattered on about what happened today.

“Oh, right! Today, Godmother taught us the Half-Sword Twin-Saber Society, you know?”

“The Half-Sword Twin-Saber Society… what's that?”

“Oh, I guess you wouldn't know, Qing'er. Godmother said that she enjoyed seeing the passion, and suggested we form a small group. So we came up with a name together.”

When Nan-gong Shencai promoted the Nine Swords Club name, Gong Sun-Yaoyi shyly raised her hand to agree. The Nine Swords Club, a club to hone their swords. 

Then, Peng Chaolei argued that they should use the path (道) character and call it the Nine Paths Club, along with Peng Daesan.

It was obvious what a saber wielder's intentions were when she pushed for 'Dao' (Way/ Saber) character. 

So they got into a loud argument—about sabers, swords, and how someone was pretending to be both—and apparently, someone let slip that a certain person was basically acting like a bat, flitting between sides.

That's how they ended up deciding on the Half-Sword Twin-Saber Society.
 
There was also a fierce debate over whether it should be Twin-Saber Half-Sword Society or Half-Sword Twin-Saber Society. But since 'swords' usually come first in title, Peng Choryeo agreed that the 'blade' should yield (not really), and it was decided to be the Half-Sword Twin-Blade Society.

“What the… okay…”

Regardless, Qing was too tired.

In one step, she took off her top. In two steps, her skirt. And in three or four steps, her undergarments were tossed aside. She flopped onto the bed.

“Qing'er? You should lie down properly. It's getting warmer, but you should cover yourself with a blanket.”

"Do it for me…"

Tang Lan'ah was also a martial artist, so lifting and placing A-Qing properly wasn't a difficult task. Normally, when people are being helped, they unconsciously use their strength to assist, but A-Qing was already drifting between sleep and unconsciousness.

Completely limp, Qing slumped, and Tang Lan'ah ended up struggling to help her in the middle of the night.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing woke up with a numb arm to find it was still dark, in the middle of the night. She soon found out what had happened: Tang Lan'ah had been sleeping while pressing down on Qing's arm, her face buried in her neck, breathing softly like a child.

When she didn't know Tang Lan'ah, her breaths had been annoying. But now that they were close, the sound of them against her ear was calming. Besides, it wasn't hard having Tang Lan'ah on top of the strongest body in mankind. The warmth was comforting, and the slow, steady beat of her heart was reassuring. At least while they were touching like this, the ending wouldn't suddenly be 'It was all a dream'.

\textit{What kind of powder did she use that made her smell so good? Ah, I want a cup of warm milk.}

Qing smiled and closed her eyes again.

And then she opened her eyes again feeling refreshed, as if yesterday was just a dream, like a dream… yesterday, aaaaahhh…

Qing shuddered and trembled. It was a terrifying experience that made her legs go weak and her head hurt. And she had to do it again? Nineteen more times?

Wasn't it better to train for twenty years?

A-Qing was seriously pondering this when Tang Lan'ah sat up groggily.

A-Qing smiled gently and greeted her, "Lan'ah. Did you sleep well?"

"Huh? Huh?"

Tang Lan'ah was now looking dazed. The poor girl had just woken up to see a radiant smile up close, which was very harmful to the heart.

Tang Lan'ah's face turned crimson red as she buried her head into the pillow.

"Huh? What's wrong?"

"No, it's nothing. It's not. I'm not, so."

"…Why are you like this first thing in the morning?'

Thanks to Qing's transcendent martial hearing, she caught the barely muttered words:

-…son-in-law… serve the family… excellent servant for the clan…

And then—son-in-law? Her mind lit up.

"Ah. What time is it? Lan-ah, I'm leaving! Master must be waiting."

Qing quickly put on her clothes and rushed out of the room.

Using her peerless Thousand Li Flight technique, she opened the door to the bathhouse, and the aroma of various fragrant herbs filled her nostrils.

Tian Youxue, who was fanning the fire under the bath, spoke with a pout, "What, I told you to come after lunch. Why are you here so early?"

"Oh. Did you? I was almost unconscious yesterday."

"Hmm. I might not have. I was too."

Looking at Tian Youxue, his complexion was dark and he looked completely exhausted.

"Master? Are you okay?"

"It takes all day to look after the fire just to make a single dose of medicine. How much more effort do you think it takes to heat up an entire bath?"

"Hmm. I appreciate that, but don't you usually say it's nothing?"

"Hmph. If you've suffered, you have to make sure others acknowledge it. I made a fuss all night for my disciple, so you obviously need to know that."

"Hehe. Thank you."

Despite being exhausted and passing out yesterday, he had woken up in the middle of the night to concoct a new medicine. It was truly something she was both grateful and apologetic for. The resentment from yesterday melted away from Qing's heart. It was all according to Tian Youxue's plan.

His saying to come after lunch yesterday? He didn't. He wanted her to come early in the morning to see him exhausted from making the bath. 

In fact, Tian Youxue knew his master very well. The harsh training and his master's taunts had turned into resentment. The saying that hate was passed down through generations fit perfectly, and that was why the relationship between master and disciple of the Divine Thiefs was often a friendship akin to love and hate.

But when Tian Youxue took on a disciple and tried to get revenge for all he had been through, he decided that it would be better to be respected rather than to have a moment of pleasure. However, he did not give up on having fun. He was just being a good master, doing all the things he thought a good master did, while thinking of tormenting his disciple in the future.

But no matter how dark or white his heart was, the fact that he had poured his heart into it was true, so Qing considered him to be a truly grateful master.

"Hmm. It smells good. Hmm. Smelling it makes me, somehow, hungry…"

At the same time, her stomach rumbled.

Tian Youxue chuckled and tossed her something.

"Hmm? What's this?"

"Yam."

Qing looked down at the clean, peeled yam in her hand. It had a slimy, unpleasant texture, but it had a kind of unique plant aroma, a delicious smell. She took a bite and it was crunchy and hard like a raw sweet potato, but also sticky and chewy at the same time.

"Hmm. It's surprisingly edible?"

"A young lady from a noble family can even eat that? It's pretty bland, and you wouldn't eat it raw unless you were really hungry."

Yams had a bad texture and taste. He had only tossed it at her out of spite, not actually expecting her to eat it. In fact, Tian Youxue, who had been raised in luxury, couldn't eat it. Despite looking unruly, he was the son of a prestigious family and a professor at the Hanlim Academy.

"Raised in luxury? Who? Haven't you heard that I used to be a a beggar?"

"Oh, really? I thought that a young lady with such grace must be the precious daughter of a wealthy and powerful family."

Tian Youxue smoothly turned his near slip-up into a compliment. Qing, not noticing it, giggled.

"I guess I do have that noble air about me."

"Noble air my ass. I'm the son of a prestigious family that has held a rank of over five for generations. Do I look like that?"

"Shall I be honest?"

"You've already said it all…"

Since she was already here, Qing chatted and helped with the making of the bath.

They grinded yam, mountain yam, and Chinese yam, then finely grinded onions, green onions, and lotus roots. And then, taro…

"Master? Are you sure you're making a medicinal bath? It's starting to look like vegetable porridge."

"I told you, I'm not good with medicine. I'm just following the recipe, I don't know why I'm putting it in."

"Is there ginseng in here? I smell ginseng."

"Ginseng? Ha, do you know how many roots of hundred-year-old snow ginseng went in there? I also added a good amount of Rebirth Pills and two Heavenly Purity Pills. This is an elixir bath. It's an elixir to be absorbed by the body, not the mouth."

"Oh, an elixir. Come to think of it, I've never had an elixir before. Wait."

Suddenly it struck her. When she was in the Demonic Cult, didn't the alleged Supreme tell his subordinates to give her all the elixirs along with the Fairy Arts?

\textit{Why did only the martial arts come, and not the elixirs? Did someone steal them? }

Of course, the subordinates who only pretended to listen to the fake Supreme Leader had no reason to give Qing the precious elixirs. They gave her the martial arts because it didn't matter if she learned them, since she could never go back to the righteous sect.

In the meantime, the bath was completed.

"Elixir baths should only be given to disciples who have learned the Awakening Divine Art. The only reason to have them absorb it through the skin is for the purpose of cultivating the Awakening Divine Art. Otherwise, it's better to just eat it raw. One bath like this will take you straight to the Fifth Level of mastery."

"Wow. Fifth Level? That quickly?"

"All the elixirs here together are worth about two hundred gold coins. Frankly, I don't really need to do this for a disciple. Two hundred gold coins is a bit much for even a Divine Thief, isn't it?"

It was him saying that he was doing it especially for her.

A-Qing, moved to tears, bowed deeply.

"Ah. Thank you, thank you so much. This disciple will engrave master's grace into her bones."

"Hmph. Don't engrave it in words, engrave it with your actions. And you might even reach a level higher than the Fifth with your capabilities. You sucked all the Abyss of Trial Elixir yesterday. Originally, most of the elixir is not absorbed, so it's a waste. That's why I don't usually do this."

After seeing Qing sucked all of the Abyss of Trial Elixir, he thought that she could absorb all the elixir bath without leaving any behind. In fact, it would be much better to slowly give her the materials over the course of a year or two rather than make an elixir bath. It was a trump card used when a successor was old or sick, or when they needed an extreme measure because their meridians were completely blocked.

"Okay, now you should eat lunch before you get in the bath."

"Oh. Then, what should we eat for lunch? Hmm, I'm strangely craving milk porridge today. How about that?"

"Why would you go out to eat when I've made a delicious restorative soup? I put in all sorts of good ingredients, so you should try some. I'll take a little out and boil it with rice."

It was both Qing's bath water and lunch. Anyone else would think that was a very disturbing thing to say, but Qing just smiled brightly.

\textit{Wow. That sounds delicious.}