\chapter{Let's Have a Spar (8)}

Back in Qing's hometown, some funny old bastard\footnote{Charlie Chaplin} once said this:

'Life, when seen up close, is a tragedy. But from a distance, it's a comedy.'

And this moment was exactly that for Qing.

From afar, she looked like some idiot who got a well-deserved lesson after messing around at the dinner table.

But up close?

It hurt. It hurt like hell. So much pain it drove her mad.

"Well… Qing'er doesn't respond to anesthesia, so… there's really nothing I can do."

She'd sliced her tongue clean through. Normally, that would need to be stitched back together.

But if anesthesia didn't work, there was no way to pull it off safely.

"So what, we're just going to leave it like that?"

Peng Daesan asked, staring at Qing, who was swallowing down mouthfuls of her own blood.

Tang Lan-Ah shook her head.

"If even Guan Yu\footnote{Guan Yu allegedly had his left arm operated to extract an arrow. He did it while having feast with his men.} had been told to get his tongue stitched without anesthetic, he probably would've just passed out."

The tongue was packed with nerves—so sensitive that no matter how tough you were, no sane person could endure that kind of procedure.

And besides, it was risky just to attempt it.

Because when people feel pain, they clench their teeth.

And if you're stitching a tongue while someone clenches their jaw… that tongue might get completely severed.

So Tang Lan-Ah's prescription was simple: dump a mountain of blood-stopping powder into Qing's mouth.

Once the bleeding stopped, her tongue would heal quickly. The tongue was one of the body's fastest-healing organs.

But… that powder was bitter and spicy as hell.

Qing just looked like she was about to cry.

"Lan-ah…"

"Hmm? What is it?"

"Do you… think I can shtill eat dinner…"

Tang Lan-Ah slapped Qing's shoulder so hard it echoed.

"Seriously? You split your damn tongue in half and you're worried about dinner?! Does it not hurt?!"

"It'sh not… quite half…"

"Tch. You're drinking milk with honey for the next few days. You think your tongue just sits around doing nothing when you chew?"

The tongue didn't just chill while you ate—it moved constantly, pushing food between your teeth and helping you chew.

In other words, she wasn't allowed to chew anything for now.

"Ah… nooo…"

The light faded from Qing's eyes.

The look of a soul in despair. Dead eyes.

"And no sparring either."

"Why…"

"Because you can't do intense movement. What if the wound reopens? You won't be able to eat your precious food again and you'll be back at square one."

"Owkay…"

"And no talking, either. Every word you say adds another hour to your recovery time."

Qing nodded with vigorous enthusiasm.

Tang Lan-Ah came to a new realization that day:

Qing would do anything if you used food as leverage.

"Don't let your head go lower than your heart or you'll get blood pooling. Use a high pillow and sleep on your back. No sleeping on your side."

Nod. Nod.

And so Qing, looking like someone who'd lost the world, sat sulking in a corner of the training hall, watching the others spar.

Then, a thought crossed her mind—

\textit{Wouldn't that old martial arts book vendor guy probably know a training method she could still use?}

She headed toward the bathhouse, half-hoping, half-dreading—

And of course, there he was, Tian Youxue, sprawled out on a mat, snoring.

As soon as Qing stepped closer, he opened his eyes naturally and sat up.

"What's this? Finally here to perform your formal disciple's bow?"

Qing shook her head.

Tian Youxue frowned.

"What, cat got your tongue? Why the silent head shake?"

"Cut my tong…"

He burst out laughing.

"Ha! Bit it while eating, huh? Everyone goes through that once. I've stabbed myself so many times. Split my lip clean in half once."

"……"

"What? Wondering why I didn't warn you? Even if I had, you think that would've stopped you? These things only make sense after they happen. Even if I told you a thousand times, you'd still end up doing it anyway."

"……?"

"How'd I know just from your face? That's called experience, girl. Also, your face is easy as hell to read."

"……"

"I don't know what that means. Use your words."

So Qing spoke slowly, carefully:

"Training… that doesn't… move body too much…"

"You're asking if there's a training method that doesn't require intense movement? Ha. Judging from that mess on your face, you got yourself good. And even like that, you still want to train?"

"Yes."

"Well… there is a method that suits you perfectly."

Qing's face lit up.

Tian Youxue snorted.

"And why the hell should I teach it to you? You're not even my disciple. You're a funny one. Unless you're ready to do the disciple's bow—"

Before he could even finish the sentence, Qing gave a shallow bow.

She kept her head raised slightly, remembering not to lower it below her heart.

"Damn, you're stubborn as steel. Fine. Here. Take this."

Tian Youxue pulled something from his robe and tossed it to her.

It was a small, intricately carved Buddha statue, so detailed that even the folds in its robes and tiny decorations were perfectly rendered.

Even Qing, who knew nothing about Buddhist art, could tell it was valuable.

"You've still got the Azure Blade, right? Go to the kitchen, get a big fat radish, and carve one just like this."

"……"

"Does it help? You said you wanted to master softness, right? Softness comes from precision and sensitivity. People go on about Flowing Petal Integration and Cloud-Splitting Tendon Techniques and all that crap, but in the end, it's all about exacting, delicate angles. Flowing, redirecting, returning. That's all it is."

"……?"

"Strength is just… strength. More power, more speed, more force. Sure, your body's strength has limits, so people refine their technique to get more out of what they have. But compared to softness? That's nothing. That's why there aren't many martial arts focused on softness. They're just too damn hard."

Styles based on softness were notoriously difficult to master.

And if your level wasn't high enough, the techniques were practically useless in actual combat.

"……!"

Tian Youxue understood even Qing's silence.

"What? Surprised I sound like a real expert? I'm just a lightweight old man. All those so-called masters trying to act all serious—it's laughable. Since when did pride feed you?"

Qing nodded so hard it was practically violent.

It was sincere agreement—full and wholehearted.

Tian Youxue grinned.

The more he looked at her, the more he wanted her as a student.

"Look at you, understanding your master like that. Funny how the ones most obsessed with their dignity are always the biggest clowns. You really sure you won't be my disciple?"

Qing bowed again.

Tian Youxue clicked his tongue in frustration.

"Then quit bothering an old man while he's trying to rest. Always showing up when you need something. Hmph."

Qing felt a pang of guilt and forced herself to speak clearly.

"Thank… you…"

"Yeah, yeah. Whatever."

Tian Youxue said his piece, then lay back down and shut his eyes again.

Qing stood there awkwardly for a while, unsure what to do—until she heard the snoring start back up. That was her cue. She quietly slipped away.

A little while later, Qing returned to the training grounds with an entire box full of radishes she'd picked up from the kitchen.

"What the—! Qing, you're not supposed to eat!"

Qing narrowed her eyes.

Did they really think she was just some food-obsessed creature here to devour everything in sight?

Besides, if she were going to sneak a bite, why the hell would she gnaw on raw radish of all things?

She shot them a dirty look and sat down, taking up position as she began carving.

But… hmm. It wasn't going the way she'd hoped.

She'd expected carving a Buddha statue to be hard, sure.

It's not like she had any experience sculpting, and the one Tian Youxue had given her was incredibly detailed.

Still, she'd thought, \textit{If I just keep at it, maybe I'll get somewhere…}

Yeah. Right.

The problem started with the tools.

There was a reason sculptors didn't just use one knife. Proper carving knives had short, specific blades shaped for precision—each with its own role.

Some were for carving planes, others for curves, and the smallest were for fine detail.

They were short for a reason: you had to grip them close and tight for delicate work.

But the Azure Blade? That thing was long for a dagger, and so sharp it cut radish like tofu just by looking at it.

Forget carving a Buddha—Qing couldn't even get the basic shape down. All she did was waste radishes.

"Messing around with food again, huh?"

Qing scowled in reply.

Peng Daesan just shrugged and went back to sparring with his sister.

Since Qing couldn't participate in training, Tang Lan-Ah stuck close to her instead—and she was having the time of her life.

"I used to carve a lot too. It's amazing for improving your hand skills. Really helped when I was learning hidden weapon techniques."

That made Qing trust the book-vendor geezer's method just a little more.

Tang Lan-Ah pulled out a throwing blade and casually carved up a radish, roughing out a fairly decent Buddha figure in no time.

Sure, it only had the general shape and pose—it was nowhere near the exquisite detail of Tian Youxue's version—but still impressive.

"There's a trick to it, see? You start with a big chunk and balance it out. This'll be the head, this the body, this the feet. Focus on the basic proportions first."

And with that explanation, Qing felt like she was starting to get it.

But 'feeling like' meant absolutely jack.

If understanding carving was that easy, the world would be full of master sculptors.

Still, Qing didn't give up.

Not because she was some tireless, noble warrior.

But because sitting around doing nothing wasn't an option.

Even if it was just a bit of progress, she had to improve.

A little tongue injury wasn't enough to stop her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A few days earlier—

Yun Yuanling had a look of absolute horror on her face.

"Xinpa, are you really planning to bring that filthy, ugly dog with us?"

"It's fate. We crossed paths, so I can't just abandon it."

"Dogs, once they become strays, bite people! They're wild animals, not pets!"

Xinpa chuckled.

"You worried this old lady's gonna get bitten?"

Yun Yuanling tried again to talk her out of it.

And for someone who usually faded into the background like water into wine, she was shockingly passionate now.

"Dogs smell! And that one's got long hair—it'll shed everywhere. Plus, the moment we take it outside, it'll come back covered in fleas, ticks, bugs, and literal dirt."

"Pfft. Who asked you to take care of it? It's my house, and I'll keep whatever I damn well please. Why's some stuck-up girl acting like she has a say?"

"Oh, come on, Xinpa! Can't you show some consideration for the people you live with? I hate animals. They're revolting!"

"Tch. A freeloader acting picky, are we? If you hate it so much, why not move in with the Poison Demon or the Sword Demon?"

"You're being cruel… This is what it means to be homeless… so powerless…"

She wiped at her eyes as if crying—but her expression quickly turned dark and full of venom.

"If you insist on keeping it, then train it well. I don't want to see its nose anywhere near the annex. If it sets one paw in there, I'll butcher it and toss its carcass to the pigs."

And now—

"Oh my, Chougou! Did you roll in the mud again? No, no. Sit! Good boy—see how well he listens? Now, let's get you washed up."

'Chougou\footnote{醜狗}' basically meant 'Ugly Dog'.

You could argue it was a bit much for a name…

But honestly? One look and it just fit.

"Chougou? No—his name is Dafu\footnote{大福. lit ' great fortune'}. Dafu, got it?"

"Come now, Xinpa. Doesn't Chougou just suit him perfectly? What do you think, Chougou?"

Ruff! Ruff! The dog barked and dropped to Yun Yuanling's feet, wagging its tail.

"See? Even he likes it."

Xinpa's face twisted.

"And this is the woman who swore she'd butcher him if he even stepped near her annex?"

"Hm. Let's just say… I had a change of heart."

"A change of heart doesn't turn your whole face into a different person. You're shameless."

Yun Yuanling gave a faint smile.

"Xinpa. Have you never felt it? That bone-deep, soul-crushing loneliness—even while surrounded by people? That feeling of being utterly alone in the world?"

"Hmph. That's just life. Everyone lives alone."

"You wouldn't understand. You don't know what it's like to be different. To feel like the only person in the world who doesn't belong."

"That's just how people are. You can know the flow of water, but never someone's heart. No matter how well you think you know someone, there comes a moment when you realize—you never knew them at all."

Her voice was full of regret.

And Yun Yuanling's smile grew deeper.

"What I meant wasn't about ‘feelings'—it was about something more essential. Being truly alone in the world… that's a punishment no one deserves. I couldn't take it. So I decided to change that. Chougou, do you understand me now?"

Ruff! Ruff!

The dog barked again, as if it understood perfectly.

And Yun Yuanling's smile turned even softer.
