\chapter{Let's Have Some Fun (4)}

Qing's Moonlight Sword (No. 10) was a vicious weapon that, no matter who classified it, would be called a heavy blade.

With the tip of the blade leading, Qing accelerated with rough steps that seemed to shatter the earth, resembling a steel carriage pulled by eight valiant steeds.

"Keoheok."

The Moonlight Sword easily pierced through the belly.

The three-foot, three-inch blade instantly penetrated the abdomen of the Sapa1 martial artist.

The Sapa martial artist was halted by the blade's guard.

Crack! The bastard's forehead collided roughly with Qing's, which was as smooth as the full moon.

"Sa-Save-"

But Qing's charge did not stop.

Following that was a, Thud, and another, Thud.

After piercing through three sturdy men in a row, Qing's reckless charge noticeably slowed down.

But, no, one more, I can do it.

"Euryahhhhhhh!"

Qing yelled and stretched out both hands.

Three people in a row, with a total of six legs, floated in the air, and then, Thud!

"Kill her! Kill her!"

"Young Lady!"

The blade should not come out in the same direction it entered.

But even for Qing, it was not easy to pull out a sword that had pierced through four Sapa martial artists in a row.

This was because when something penetrated their bellies, people instinctively grabbed onto it tightly with their hands and held on for dear life.

One of the Sapa martial artists raised a great sword.

Qing immediately let go of the hilt and bent her legs.

Thud! As if splitting firewood, the fourth Sapa skewer's head split in half.

Collateral damage!

"Uh, ugh, keoheok!"

The warrior, startled by the sudden death of his comrade, made a painful groan as a sudden impact hit his solar plexus.

It was Qing's head that had butted the Sapa martial artist's solar plexus.

Qing pushed forward like a charging bull, raising both arms in a triumphant gesture.

The Sapa martial artist's body floated up and fell, along with his comrades, in a heap.

And with three quick steps, she stomped her left foot on the ground, raising her right foot high.

Her ankle, knee, and hip rotated, gradually amplifying the rotational force. With the leg strength said to be three times that of the arm, she delivered a powerful kick!

It was a kick aimed precisely at the back of the fallen Sapa martial artist's neck.

The head, separated from the spine, shot out like a cannonball and struck another Sapa martial artist in the face.

"This house sure is good at defense!"

Qing, talking utter bullshit, raised her knee and vertically stomped down.

She stepped on the Sapa martial artist's arm just above the elbow, causing the lower arm to bounce up due to the reaction force.

The tendons pulled, causing the fingers to spread wide, and the straight sword he was holding was thrown upwards.

Qing leaned her waist and snatched the straight sword.

A straight sword was a weapon that extended a kitchen knife in all directions.

The tip was sharp, allowing it to stab, but its center of gravity was concentrated on the handle, making its destructive power less effective.

Of course, if one had sufficient strength, there was no need to worry about destructive power.

"You're back! Hell's Demonic Blade!"

If a straight sword had a conscience, it would have questioned, ‘Huh? Me?'. But unfortunately, weapons do not have egos.

The cheap straight sword, instantly transformed into Hell's Demonic Blade, bit into the enemy's shoulder and exited through the opposite flank.

The Sapa martial artists retreated, taken aback by the brutal handling.

You're retreating? Then I'm coming for you.

Qing pushed off the ground with all her might.

The blue uniform trailed long, stretching out, and at its end, Qing's toes emerged, kicking up one of the bastard's chins.

It resembled the kicking techniques used by Na Yanggyeol, perfectly imitated by Qing.

The Sapa martial artist floated up half a zhang.

With a kick that went straight up to the chin, the neck bones immediately gave way, causing the head to dangle close to the back. Instant death.

With her left and right foot in a straight line and her upper foot soaring above her head, Qing stomped down with her full force, causing her body to disappear in an instant.

With a stomp that seemed to crater the ground, Qing soared into the sky.

She flew a zhang into the sky, pulling her left arm.

Twisting her body like a dolphin lying in the sky, Qing gently pushed her left arm.

Duuuuung……!

A grand, booming bell sound, which was the vibration from her body, rang out as a massive amount of Inner Qi was instantly expelled, causing a group of Sapa martial artists to suddenly disappear.

The shattered bones and flesh of three people filled the handprint left on the ground by the Buddha's Palm.

It was as if a palm had swatted down flies.

Suddenly, the sound of a majestic bell echoed across the battlefield, drawing everyone's attention.

"Heavenly Flower Sword! It's the Heavenly Flower Sword!"

Qing, who had soared up in response to the recoil of Buddha's Palm, descended gracefully to the ground with the elegant posture of the Yue Maiden Steps.

Right into the middle of the enemy lines.

Gang Suyang, the Sect Leader, snapped back to his senses.

She had said she would lead unknown Masters from the Royal Household to attack the rear, not to jump right into the enemy lines.

Then why?

The greater the disturbance in the rear, the more confusion it would cause in the front lines.

There was no need to attract attention so conspicuously, yet she had used Buddha's Palm to draw attention. It meant she had willingly put her life on the line.

Something hot surged in Gang Suyang's chest.

"The Heavenly Flower Sword is over there! The leading Rising Star of the Orthodox Faction is surrounded by enemies! Will our Seniors just stand by and watch?!"

At Gang Suyang's cry, the disciples of Gyerim and Jangsan responded with a shout and rushed forward.

This meant that the martial artists of the Yeom Gang and the members of the Black Bear Squad at the forefront had begun to falter and retreat.

Qing was just having fun on her own.

So, Qing realized belatedly.

With the flow of the atmosphere to her left, right, front, and back, she realized she was completely surrounded by enemies.

Even though she was Transcendent-something-something-Qing, she couldn't go on a solo rampage in a party of First-Rate martial artists with the occasional Peak Realm Expert.

However, the enemies were still dazed, trying to come to terms with the sudden appearance of an enemy that had dropped from the sky.

Qing invoked the cold energy of Bingbaek.

A dragon's head emerged from her shoulder, wrapping around her left arm to her hand with the sound of ice clinking.

And at the moment the translucent ice dragon reached its destination, Qing's palm also reached the chest of a Sapa martial artist.

Instantly, all the ribs shattered and the heart burst, causing the chest and back skin to meet in a gruesome encounter.

This was the mighty power of the Ice Cold Divine Palm!

It was hard to tell where its destructive power had anything to do with ice techniques.

The corpse quickly froze over, so maybe the Ice Cold Divine Palm was a martial art that rapidly cooled corpses.

A gap!

I'll just, slip out through here.

The Sapa martial artists didn't have the presence of mind to throw pink projectiles, so Qing took advantage of the gap and kicked off the ground.

With the first step, she stepped on an enemy's shoulder, with the second, an enemy's head, and with the third step, she used the most ferocious footwork of the Celestial Demon's Dominating Stride, Quaaang!

As the head of the Sapa martial artist exploded in all directions without a trace, Qing's body shot through the air like an arrow.

Meanwhile, Gyeon No screamed in anguish.

"Young Lady! Nooooo!"

There was no time to stop her as Qing instantly infiltrated the enemy lines, soaring into the sky and disappearing into the middle of the enemy camp far away.

"Damn it, Changyeo! Gakdak!"

"I know!"

The two knelt down on one knee each with perfect coordination.

With an agility that belied his age, Gyeon No spun like a swallow and landed on their palms on their knees. Then, the two Transcendent Realm Masters straightened their bodies with all their might, launching the old man.

It was a human catapult, or to put it simply, a two-man launch.

Gyeon No was shot at a sharp angle.

"Young Laaaaady!"

He attached a cry full of longing, like a traveler searching for his granddaughter, to the end of his shout.

Then, he met the very Young Lady he was so desperately looking for. Their eyes met in mid-air as Qing, who had escaped again, was shot back to the rear.

In that moment when their eyes met, time seemed to stop as the two, old and young, slowly drifted and communicated with their gazes.

‘Young Lady? Why are you here? Where are you going?'

‘Huh? Gyeon No? Where are you going? That's the enemy lines?'

"Young Laaaaady!"

The shout was the same, but the emotions within were different as it rapidly faded into the distance behind Qing.

Tak, Qing, who had returned to the rear, saw Changyeoin and Gakttagwi looking at her with bewildered expressions.

What? If Gyeon No flies, shouldn't the Young Lady come back? What's going on with this arrangement?

At that, Qing snorted.

"Well, Gyeon Grandpa, even if he is an Unrestrained Realm Master. How could he just run off like that? How excited must he have been to just fly off like that? What are you doing? We need to go save him quickly."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When one mounts a running horse, it is hard to dismount.

Since Prince Suxi had already given away his son, along with a large army, he was destined to run all the way to the end.

Therefore, he decided to follow his younger brother's advice.

To make use of the martial artists, or something like that.

In fact, even if he hadn't heard the advice, seeing Prince Deokhyun threatening him by bringing a group of Masters, Prince Suxi had gained a great insight.

I see. A distant army cannot protect me from martial artists nearby.

But the Orthodox Faction, huh?

Anyway, they are all just gangsters with swords, so was there really a need to distinguish between Orthodox and Unorthodox?

Thus, Prince Suxi summoned his officials and asked for their knowledge of the martial sects in Gwangseo Province.

A mere errand boy in the marketplace might know the ecology of Wulin, but how could a Prince be expected to know such things?

However, in reality, high-ranking officials, martial artists, and commoners were largely ignorant of each other's affairs.

For example, non-martial artists might think that Daoists in Orthodox sects would spend their days sitting in meditation under a waterfall, engaging in some mysterious and wondrous training to cultivate their path every single day.

However, in reality, even the disciples of the Nine Sects would often gather together to play childish pranks. And if someone started telling a dirty story, they'd all perk up their ears with reddened faces.

Those born as martial artists or from wealthy scholar families did not understand the lives of commoners.

They didn't know why they would wear such smelly, oil-stained rags, thinking, ‘Why? Do they not have clothes? Why don't they wash them?'.

They didn't understand why they would eat such unappetizing clumps of steamed grains on the roadside, thinking, ‘Why? If they don't have grains, shouldn't they just eat meat?'.

They had no idea where they got their money to live on, so they just assumed they were digging up dirt in the mountains and fields like animals.

And non-officials thought that officials did absolutely nothing.

They thought they just sat around receiving bribes and occasionally enjoying luxurious entertainment at some gisaeng house, fondling the breasts of gisaengs.

Of course, this was true.

Therefore, the evaluations of the officials were as follows.

"Those of the Orthodox Faction are arrogant with their stiff necks, not knowing how to bow. Even in front of government officials who work for the country, they do not know how to lower their heads."

"Those bastards even interfere with the work of the government."

"They dare to judge in place of the law, taking it upon themselves to capture and kill people. They are truly outrageous."

"They even dare to extort the nation's taxes. They are terrible."

The evaluations of the Orthodox sects were quite poor.

In comparison…

"Although they are called Unorthodox, they are those who know what loyalty is, are they not?"

"Though they are martial artists, they rush out barefoot to show respect when they see an official and are cooperative in the affairs of the nation."

"They even collect taxes on behalf of the officials, so it's a great convenience for the officials in districts where large Unorthodox sects have settled. They are admirable people."

Surprisingly, the evaluations of the Unorthodox sects were high.

So Prince Suxi thought.

Then, wouldn't it be better to use those from the Unorthodox Faction?

They're obedient and loyal.

If they have a history of helping with government affairs, wouldn't they be suitable for use as semi-official experienced workers?

The one who pulled Prince Suxi out of the quagmire was, unexpectedly, the figurehead, the Gwangseo Provincial Governor.

"You should use martial artists of the Orthodox Faction."

"Why is that?"

"Since the Unorthodox bastards give bribes to the officials, of course their evaluations are good, are they not? But what in this world does not come with a price? They're trying to hide their even dirtier aspects by giving bribes, so Your Highness should not wield a sword that is already stained with filth."

It was sincere advice from the Provincial Governor, who had been living comfortably by entrusting his duties to the Prince while enjoying the prestige.

Of course, that comfortable life also came with a price, leading him to become a traitor. Thus, the Provincial Governor's words were filled with heartfelt sincerity.

"I see. You speak the truth. The sages also said that good medicine is bitter to the taste and a loyal retainer is a thorn in one's side. I am fortunate to have at least one loyal retainer by my side."

"I am overwhelmed by your grace."

The Provincial Governor bowed deeply.

Of course, the Provincial Governor wasn't speaking out of heartfelt loyalty. Since he had already become a traitor, he was seizing the decisive moment to ensure he would be dismissed from his position as Provincial Governor but remain a loyal retainer to the Prince.

"By the way, I heard that Nanning City has been noisy lately? I didn't pay much attention to it because I heard it was just a spat over food between martial artists. Now is the time to bestow grace, so it may return as loyalty."

"I will summon the Regional Inspection Commissioner and the Guard Assistant Commander." 