\chapter{Let's Have Some Fun (8)}

The cells of the local authorities were actually quite lax.

At best, they were just brick houses with straw laid out, divided into sections by wooden bars, so if one were determined to escape, even a strong adult male, not just a martial arts expert, could probably break out.

After all, if one were to charge with their body weight, the wooden bars would eventually splinter and break.

Therefore, if one had some martial arts training, escaping wouldn't be that difficult.

Of course, that was because it was just a local authority's cell.

The holding cells of such places were temporary detention facilities, similar to police station jail cells in Qing's homeland.

The real prison of the Ministry of Justice was not so easy to escape from.

That was why the Unorthodox Faction martial artists were also quietly waiting.

No trial had been held, so no sentence had been passed, and they weren't being transferred to the Ministry of Justice, so it seemed they weren't being sentenced to severe punishment.

The jailers didn't provoke them either. In fact, they were nowhere to be seen, probably intimidated by the aura of the Unorthodox Faction members.

They were even provided with meager meals on time.

So, for now, it was all about patience, and more patience.

Moreover, there was someone who was boasting loudly.

It was the Salt Gang Leader, Yo Hwancheol.

"Ahem. There is not a single official in Namnyeong who has not received silver and gold from me. They won't keep us here for long. They're probably just being cautious because of the authorities' face, not wanting to release us immediately. Isn't that right?"

But Jo Gwang-ang didn't seem to trust him.

"It's already been three days. Are you sure? You said we'd be released soon, didn't you?"

However, Gang Leader Yo confidently thumped his chest.

"Just trust me, I tell you. Moreover, the head jailer here calls me Big Brother. I wouldn't be surprised if they came right now and told me to leave-"

Creeeeak!The sound of the iron door scraping against the floor cut off Yo Hwancheol's words.

And then, the sound of approaching footsteps.

"Prisoner Yo Hwancheol. Come out."

At that, Yo Hwancheol's face lit up.

"See? I told you so."

"But why only you? Hey, when will the elite martial artists of our Four Great Evils Alliance be released?"

"I do not know. That is for the magistrate to decide."

"Now, now, don't worry. Magistrate Yoo is almost like a sworn brother to me. I'll get you out as soon as possible."

At that, the jailer opened the cell door and Yo Hwancheol leisurely strolled out.

"Ah, right. Our jailer is quite stiff with his government work, isn't he? Did I perhaps not treat you well enough? Could you perhaps take me to the Salt Gang? Then I won't be remiss in my treatment anymore. Instead, I'd like to offer some wine to our fellow Great Experts of the Four Great Evils who are suffering in this cell. Huh? What do you say?"

Yo Hwancheol was openly offering a bribe.

From behind, Jo Gwang-ang snickered.

Well, a bottle of wine might be enough to endure another day, he thought.

From the cells spread to the left and right, the sound of swallowing saliva could be heard, and some even whistled frivolously.

"But these bastards, not a single one of them came to visit even though their father is suffering all kinds of hardships in jail? Hey, is visitation prohibited? Or did no one really come?"

At that, the jailer shook his head.

His expression was one of great pity, which ignited a fire of anger in Yo Hwancheol's heart.

After all, how dare a lowly jailer, who received only a few coins a day, pity the Lord of a Great Noble Clan?

"Ha. This son of a bitch. What's your name? I tried to go easy on you, but you're really pushing it, huh? With just one word from me, even the head jailers will bow and scrape. Do you think I'm some pushover because I'm being quiet? Ha. I'm speechless."

"If you're so close to them, then you must know the layout of the government office well, right? I don't think you need an escort. And you are only temporarily released, not fully released. Tsk."

The jailer just said that and walked away on his own.

What insolence to dare act like that towards this Yo Hwancheol! Although anger surged, he couldn't cause bloodshed inside a government office, no matter how good his connections were.

So, you arrogant fucker, just wait and see if you can still act so high and mighty after I show you what happens to your parents and children.

As he was seething inside and heading outside, a sudden question arose.

Temporary release, not just release?

Aside from attending a funeral while in prison, I've never heard of anyone being let out and then coming back in.

As that thought occurred to him, Yo Hwancheol's heart sank.

No way, it can't be, he thought as he almost sprinted through the government office and rushed out the main gate.

However, Yo Hwancheol's urgent return home was stopped by external forces, namely the martial artists forming a line outside the government office's main gate.

"Where are you going in such a hurry?"

Asked Gang Suyang, the Sect Leader of the Gyelim Sword Sect.

At that, Yo Hwancheol's expression contorted.

"You bastards, could it be! My children! Can you even call yourselves part of the Orthodox Faction after doing this?!"

But Gang Suyang shook his head.

"I swear on my sect, my ancestors, my deceased master, and my honor that I have not laid a hand on the Yo Family's Salt Gang. The Heavenly Blossom Sword beside me will vouch for me."

"That's right, that's right."

Next to him, Myeonsa nodded annoyingly.

"Then, who, you!"

Yo Hwancheol's finger this time pointed at another person, the Sect Leader of the Jangsan Martial Hall.

The Sect Leader of the Jangsan Martial Hall shrugged, a mocking smile on his face.

"Our Jangsan Martial Hall may not have a long history, but if you wish, I can swear on all the sect leaders and my honor, as well as my children. Our Jangsan Martial Hall did nothing either. Will the Heavenly Blossom Sword vouch for me?"

"Of course. That's right, that's right."

Qing nodded again.

Even Unorthodox Faction martial artists were somewhat reluctant to make false oaths, especially when involving so many people.

Of course, they didn't never do it.

Yo Hwancheol was relieved for now.

But then, his heart was impatient.

If it wasn't those two, then even if he was just released, it wasn't a good situation.

Perhaps his brothers, who had been acting like enemies, had harmed each other, and didn't the Chief and Vice Chief seem to be whispering, holding onto his second and first sons?

"Excuse me, Sect Leader. I must hurry back because something has happened in my household. Even if there is a grudge between the Unorthodox Faction and the Orthodox Faction, should you not block a father trying to see to his family's well-being? I beg you."

"There is no need to take care of them anymore. That family is already ruined. That scoundrel, your third son, conspired with Sasa and used deadly poison with evil intent. And then the servants carried off everything of value and ran away, I hear. Tsk tsk. You should have been more generous with people. For servants to turn into a band of thieves even though their master's house is facing a crisis."

Yo Hwancheol's heart sank again.

"Then, who, who died? Yeon? Seong? Ahyeon?"

"I heard all your children died? Ah, that third son might have survived. Maybe someone else did too. This Sect Leader has been too busy to look into such trivial matters. We had a banquet to hold."

Gang Suyang continued with a cold gaze.

"And we had to perform funeral rites for our dead disciples."

At that, the martial artists of Gyelim and Jangsan simultaneously drew their weapons.

"I'm sorry. But to appease the souls of the disciples who died unjustly, I'm going to need the head of their enemy."

"Such a cowardly…!"

"Even if I am called a coward, I will endure it if it means comforting the souls of the disciples who died unjustly."

"You bastard! You came here to kill me from the start!"

Now it was not his family but his own life that was at stake.

Yo Hwancheol urgently turned around.

He was planning to take shelter in the government office.

It would have been a good idea if the main gate of the government office hadn't been firmly shut.

Moreover, the three guards who were supposed to be guarding the left, right, and center of the main gate were nowhere to be seen.

The meaning was clear.

We do not know what is happening.

We cannot see it, nor do we want to.

It was a textbook example of non-interference agreement.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Prisoner Jo Gwang-ang. Come out."

"Well, already?"

Jo Gwang-ang's lips stretched wide.

"Money really does work wonders, huh? They've already processed everything. But what about my brothers? Not yet?"

"I do not know. I was only told to release you."

"You're so rigid. How much did Gang Leader Yo give you? Since you're still so stiff, it must not have been a very satisfactory amount, right? Well, what can a lowly jailer do to deserve good treatment? They probably fed the higher-ups instead. Right?"

Despite the provocative remarks, the jailer remained silent.

"Aigh, no fun. Fine. Hey, guys, I'm going out first. I'll make sure you can get out soon, so even if it's late, I'll have a feast with plenty to drink and eat, so don't worry."

"Yes! Chief!"

"Alright. Heh heh, just wait a bit."

And so, Jo Gwang-ang walked out with a pleased expression.

Out of the cell, towards the main gate.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Namnyeong Family, nearly wiped out.

Well, since there was one Yo who was still fine, it wasn't a complete annihilation.

But that fine Yo had no intention of carrying on the family lineage, so it wasn't much different from annihilation.

So, nearly wiped out.

Three combat units of the Four Evils, almost completely destroyed.

This was because among those who came out of the government office, Qing's finger occasionally pointed at a few.

"Shouldn't we spare him? I heard he's not that bad of a guy."

"Thank you, thank you……!"

"Live kindly. If I hear you're being a bad guy next time, I'll break your arms and legs and hang you in the marketplace."

"Yes, yes! I'll live kindly!"

A warning and a release.

Honestly, it was absurd to the disciples of the Gyelim and Jangsan Sects.

How did she know who was a bad guy and who wasn't all that bad just from hearing about them?

Pointing out individual combat unit members, saying to kill this one and spare that one.

But it was a request from the Heavenly Blossom Sword.

Our Heavenly Blossom Sword wants to do it like that?

Then we have to do it like that!

Our Heavenly Blossom Sword, do whatever you want!

In a situation where the royal household and Wulin were intertwined and not seen in a good light, especially since it involved another region's royal household, not their own.

Therefore, the servants of the royal household who had accompanied Qing on the raid were described as unaffiliated experts that Qing was close to.

So, except for a few who knew the truth, the perception of the Namnyeong martial artists was as follows.

A Master who volunteered for the most dangerous tasks and went into the line of fire, yet also showed the most outstanding performance!

She even defeated Mun Jeongyeok, who was known as the greatest swordsman of Bokju and was at the Late Stage Transcendent Realm, without taking his sword.

The title of the generation's Divine Dragon, the greatest Rising Star of Wulin, might have implied looking after the juniors, but now…

Now, it was all about the Heavenly Blossom Sword.

Not just a Rising Star or a young expert, but the Heavenly Blossom Sword, a treasure of the Orthodox Wulin, surpassing even age!

And also a beauty that could be argued as the greatest under the heavens!

Moreover, kind, polite, and unpretentious!

The treatment of the benefactor by the Namnyeong Orthodox Faction became extremely cordial. As such, all that was left were the comfortable days of walking a flower path, no, lying on a flower bed, drinking and eating.

"Elder Sister! An invitation!"

"Hmm. Where is it from this time?"

"The Jeong Family, the Uiju Martial Hall, the Cha Family Academy, ah, and the Abbot of Yeongsan Temple has come in person to ask if you could write a signboard for them! And from here on are letters! This one is from the Vice-Minister of Personnel, this one is from the Lord of Gwangil, and this one is from the Governor of Hwanghyeon Prefecture……."

"Ugh. This is annoying."

After the situation was resolved, the problem was the influx of invitations.

It wasn't right to not go, but if they went, the men would make a fuss, shooting greasy, sleazy, lecherous gazes, ugh.

Moreover, it wasn't just invitations from the Namnyeong region; they were coming from all over Guangxi Province.

At this point, even writing rejection letters became a chore.

The handwriting in those replies was admired to the point of driving people to madness, so now even those asking for calligraphy were starting to swarm.

Qing jumped up.

"This won't do."

"Y-Yes, sir?!"

"If we stay here any longer, we'll be exhausted from just greeting people all winter instead of resting. Let's get out of here. It's not like we have to stay with the Gyelim Sword Sect, right?"

"Such! Words! No, sir! Elder Sister can stay forever! You can stay here for all eternity! To Gyelim, the Heavenly Blossom Sword is our benefactor! If the Heavenly Blossom Sword is here, then that is all that matters! I will do my utmost to block them! Elder Sister, you may rest comfortably in seclusion!"

Unaram spoke passionately.

But Qing had already made up her mind.

"The mission from the Wulin Alliance was to stay here because those Unorthodox Faction bastards were suspicious. Now that Namnyeong is safe, we should go to other dangerous places to help with the mission. I heard that the Jin Family is having a hard time these days."

Namnyeong had heard that the Jin Family was in a difficult situation.

It was nice to be treated with utmost respect and to enjoy this and that, being called here and there for gourmet gatherings.

But if I'm done with my work here, I think it would be much better to be in a place where I can be of help.

Moreover, since those Unorthodox Faction bastards were openly causing trouble here, who's to say things would be any different in the Guangdong Province? 