\chapter{Let's Have Some Fun (1)}

In China, ranking people was like a deeply ingrained instinct in their souls.

Just as there was a hierarchy with the Five Great Clans at the top, there was also a ranking system for the lowest and most despised individuals.

Thus, the five most menial professions gathered and thought, ‘Since no one cares if these lowly scoundrels are beaten or killed, why don't we, the lowly ones, band together and help each other to survive a bit longer?'

Even the lowly should be able to live, right?

This was the birth of the Hao Sect.

However, the Hao Sect wasn't really a grand organization.

It was just a lower-class cooperative where those who were miserable due to their low status gathered to feel a little less miserable.

It wasn't like they were gathering to make a world where the lowly were respected, waving red flags or anything.

Because if they did that, they would all die.

Moreover, there were hardly any Masters in the Hao Sect.

This was because Masters were no longer considered lowly and could go out into the bright world to live well and be treated with respect.

And the few Masters that were there were just troublemakers who couldn't show their faces under the sun.

Of course, within the Hao Sect, there was a faction that advocated for taking on big projects, saying things like, ‘Just because we lack status, elegance, popularity, and honor, doesn't mean we're broke'.

However, recently, with the downfall of the Black Spot, this faction within the Hao Sect had also lost its power.

Look at what happened to those Black Spot bastards.

They thought they were something just because they were black market merchants, acting all high and mighty with their ‘Laws of the Black Spot'. But in the end, they were just lowlifes with a bit of money. In the blink of an eye, they were utterly destroyed.

So, let's just sway with the wind.

Reeds may bend, but they do not break.

In that sense, the Hao Sect also preferred the martial artists of the Orthodox Faction over those of the Unorthodox Faction.

The Orthodox Faction martial artists would at least pay for services rendered, but the Unorthodox Faction bastards treated the Hao Sect as their underlings.

In fact, since the work done by the Hao Sect was often menial, dirty, and sometimes even evil, they were treated as part of the Unorthodox, or at best, as semi-Unorthodox.

However, the Unorthodox Alliance didn't want to acknowledge the Hao Sect, as they didn't want to associate with such lowly, common ruffians.

So, they were just lackeys.

They were considered lowly parasites that infested the territories of the Unorthodox Faction.

Despite looking down on them more than anyone else, they would use them when needed. But when it came time to pay…

"Sir. We have some information about the Heavenly Blossom Sword that you might find interesting. If you could just spare a few silvers to help these poor wretches quench their thirst-"

Smack!

The porter, Wang, had his cheek turned sharply.

How dare a lowly wretch try to extort money from someone?

Moon Jeongyeok growled.

"Say that again. What?"

"N-No, it's nothing. This lowly one must have lost his mind. Hehe, it's an honor for a Great Hero like you to use this information. How could this lowly one dare to ask for payment?"

The porter, Wang, who emptied the waste of Yuhgayeom's outhouse, wore a servile smile.

In truth, the Unorthodox Alliance's guidelines stated that a certain fee should be paid to the Hao Sect when requesting information.

This was because if they were not compensated, the results might be poor, or they might deliberately sabotage the information out of spite.

The problem was that the Unorthodox Faction interpreted these guidelines as, ‘Let's put the Hao Sect's usage fee in the operation budget and legally embezzle it'.

So, naturally, the information coming from the porter, Wang, who got a slap in the face instead of payment, was intended to screw them over.

"Yes, you said you had information about the Heavenly Blossom Sword?"

"Hehe, as you commanded, while monitoring the Heavenly Blossom Sword, we discovered something very surprising! Last night, the Heavenly Blossom Sword rented the Dragon Palace Room at the Dragon Palace Inn. Ah, do you know the Dragon Palace Room at the Dragon Palace Inn? It's the best room at the best inn in Nangyeong-"

"Enough. So?"

"But! Sir Sa's personal attendant visited the Dragon Palace Room last night. According to the maid, the Heavenly Blossom Sword greeted Sir Sa with such joy, like seeing his own grandfather, and with such politeness, like serving a senior of his sect."

"……?"

Moon Jeongyeok's thoughts momentarily stopped.

Who met whom? Why?

"Are you sure you know what you're saying? Your neck could be on the line."

"How could this lowly one dare to lie about such a matter? The Heavenly Blossom Sword reserved a room and waited with brewed tea, and Sir Sa secretly visited him late at night, at the hour of the pig1."

Words were so subtle.

And at the hour of the pig, late at night.

When Sir Sa was a senior of the Jianghu by a wide margin.

Secretly, he visited in person.

This made it seem like the Heavenly Blossom Sword held the upper hand in their relationship.

After all, it was common for the one with a request to call upon the person who could fulfill it.

"Your words must be true. I can destroy not only you, but all the sewer rat bastards in this city."

"Of course, sir."

Even when giving information, he was still treated like shit, making it clear that associating with the Unorthodox Faction was a terrible idea.

However, was a porter getting cursed at anything new?

The servile smile hid his true feelings well.

After the Hao Sect member bowed deeply and left, Moon Jeongyeok pretended to be deep in thought.

Sir Sa was in cahoots with the Divine Dragon of the Orthodox Faction?

Sir Sa was not only a master, but also one of the few physicians in the Unorthodox Alliance, making him a highly regarded figure.

Of course, there were almost no patients who wanted to receive a diagnosis from Sir Sa, as he was a human known for his fondness for handling snake venom.

But for such a figure to be in cahoots with the Divine Dragon of the Orthodox Faction?

On the other hand, it made no sense.

There was no reason for the most outstanding Rising Star of the Orthodox Faction, who lacked nothing in terms of martial prowess, money, honor, and beauty, to collude with an old Demonic Adept of the Unorthodox Faction.

But, that's right.

It was indeed more convincing to believe that Sir Sa had betrayed the Unorthodox Faction, rather than the Heavenly Blossom Sword betraying the Orthodox Faction.

For one, Sir Sa was an old Demonic Adept, so there was no issue of trust.

It would be understandable if an old man, nearing the end of his life, wished to change his identity to the White Path out of a newfound desire for honor.

In fact, unlike the old masters of the Orthodox Faction who lived well and died honorably, the old Demonic Adepts of the Unorthodox Faction often had miserable ends, didn't they?

When their skills declined with age, they were often attacked by enemies seeking revenge for past grievances, stabbed by juniors coveting their martial arts, and threatened by disciples demanding payment for years of service… It was hard for Demonic Adepts to live long, and even if they did, this was the result, making it a truly sorrowful life to be an evil person in Wulin.

However, there was not a single reason to think that the Heavenly Blossom Sword would betray the Orthodox Faction.

‘This is interesting.'

Look at that. The old man acted like he was going to do something, but he's been dragging his feet for months without any news.

That damned old man, how dare he try to betray the great alliance of the Unorthodox Faction.

And for the sake of a comfortable end to his life, no less?

Moon Jeongyeok's lips twisted.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Nah Yanggyeol had come to the Heavenly Blossom Manor on behalf of the sect to discuss the issue of the Heavenly Blossom moniker, which was quite a troublesome matter for them.

However, the reason Nah Yanggyeol had stepped forward as the representative was not because she was the Great First Apprentice Sister or the Jihwa.

It was because Nah Yanggyeol was the most ardent advocate of lookism within the Heavenly Blossom Manor, meaning she was extremely picky about appearances.

She was acknowledged to have an objective aesthetic sense that went beyond personal preference, setting a strict standard.

If the Heavenly Blossom Sword was truly the most beautiful woman under the heavens as rumored, the Heavenly Blossom Manor had no complaints about her being called the Heavenly Blossom.

Because even if the flower was outside their garden, it was still a flower.

If the flower outside their garden was the most beautiful flower in the world, their flower garden would gladly respect it.

Thus, Nah Yanggyeol's attitude was already decided before she even met Qing.

"You know what? Originally, I really hate putting stuff on my face."

Qing looked at Nah Yanggyeol's face.

She was already a stunning beauty, but with makeup, she was certainly a beauty that one wouldn't tire of looking at.

But…

Here we go again.

Qing shook her head.

"Yeah. I didn't ask."

"That's right. It's all makeup I put on to look good for my Gomtaengie. Every morning, I spend two hours looking in the mirror, applying makeup. I wonder if my Gomtaengie will be charmed by me? Will he recognize my earnest heart?"

"Yeah. He won't be charmed. He won't recognize."

"Even if he doesn't recognize it, it's fine. If my Gomtaengie can enjoy the sight of me, that's already a great reward for me."

"But who's this Gomtaengie? It's kind of a weird name for a person, isn't it?"

"Well, because he's a cute animal who spends all day eating and lazing around, eating and sleeping? He has an insatiable appetite for sweets. But in reality, he's also a ferocious beast and a clever animal. Just like someone."

The culture of affection in Zhongyuan was, in many ways, unimaginable, often making onlookers cringe.

This was especially true when it came to nicknames. The people of Zhongyuan would give their lovers the most trivial nicknames as their relationship deepened.

My Glutton. My Fool. My Piggy, and so on.

Nah Yanggyeol shot Qing a profound look.

However, it was deflected.

"You're really flirting with just your words, huh?"

"It's a truth that overflows and cannot be hidden. Now then, my Gomtaengie, shall I put this racing heart on your ha-"

Nah Yanggyeol's attempt to take Qing's hand and place it on her heart was in vain, as it missed its mark in the empty air.

This was because Qing quickly pulled her hand away.

"Oh my. You know what? Bears are surprisingly fast. Just like my Gomtaengie."

Originally, Qing was weak against those who pushed.

She didn't hate it because someone liked her, but she wasn't lonely enough to accept affection based on looks alone.

After shooing away Nah Yanggyeol, who had been clinging to her since morning, Qing headed to the disciples' dining hall of the Begonia Sword Sect, wondering what would be for breakfast and thinking that since it was morning, she shouldn't indulge too much and should just have a simple bowl of congee.

"Senior Sister! Did you hear the news?!"

"Huh? What?"

"The bastards from the Yoga Flame Sect issued an ultimatum to the Jangsan Martial Hall! They told them to come under their command!"

"What? Suddenly? So?"

"The head of the Jangsan Martial Hall has requested reinforcements from the Begonia Sword Sect! So they're discussing it now-"

"Ah. You're here. Young Lady Ximen."

Cutting off Woo Naram's loud voice, the head disciple of the Begonia Sword Sect, Do Daljeon, appeared.

"Were you looking for me?"

"Actually, I have a favor to ask. It seems the bastards of the Unorthodox Alliance have given up on the Begonia Sword Sect and are instead trying to conquer other Orthodox Factions in Nanning."

"Ah. I just heard. You said the Jangsan Martial Hall requested reinforcements?"

"Ahem, Naram, you little brat."

Do Daljeon glared, and Woo Naram flinched and looked away.

She was avoiding eye contact in response to the reproach for carelessly discussing the sect's affairs, even with a close friend.

"Since the Jangsan Martial Hall will fall, the other Orthodox Factions' martial halls will also defect from the Wulin Alliance. So the disciples of the Begonia Sect will go to support them. In case you were wondering……"

In other words, it meant there was going to be a big fight, so he was asking if she could help.

It was very welcome news.

"Ah. Then I can't possibly miss out."

"Honestly, the Sect Leader was against the Heavenly Blossom Sword's participation. To be frank, the enemy's forces are far superior to ours, and we cannot guarantee your safety, Young Lady."

"Hey, where is there safety for someone who lives by the sword? And what are you going to do with a Transcendent Realm Master if not use them? I'm just an idler who eats a lot, so I should at least earn my keep."

At Qing's banter, Do Daljeon's eyes shook.

It was easy to say.

But the enemy's forces included three combat units of the Unorthodox Alliance, their leaders and vice-leaders, and Sir Sa, a master of poison techniques.

Wasn't it a fight they couldn't possibly win?

They had barely managed to avoid the fight by using the Prince as a shield, but now the Heavenly Blossom Sword knew this too.

Yet she so readily offered to help, so it was like a sea of emotion, truly overwhelming.

Do Daljeon bowed deeply, putting his hands together.

"I will never forget this kindness."

In fact, it was a great kindness.

Qing was confident in her skills, so she didn't think she would lose in a fight.

Moreover, as a member of the Orthodox Wulin, it was simply a result of her straightforward thinking that she should naturally help the Orthodox Murim.

But if Ximen Surin had seen this, wouldn't she have been heartbroken?

Why would her disciple, of all people, throw herself into such a dangerous battlefield?

So if she didn't have to, she didn't have to participate in this dangerous fight.

To Do Daljeon, it was a decision worthy of a deep bow and respect.

However, to Qing, who was on the receiving end of such a grand gesture from an elder, it was just embarrassing.

So she just joked around.

"Ahem, kindness, you say. As members of the Orthodox Wulin, we're all family, so we should obviously help each other, right?" 