\chapter{Let's Have Some Fun (6)}

The sword of Mun Jeongyeok was a renowned blade.

It was even given the elegant name of Paryu Sword, due to its resemblance to a waving willow branch.

If one held the honor of being called the best swordsman of Bokju, using a mediocre sword would only tarnish their dignity.

Therefore, they must either use an item close to a cheap piece of hammered scrap metal.

Then, they would hear that even a cheap item held by a Master became a masterpiece.

Or use a sharp, renowned sword. After all, wouldn't the dignity of the best expert in the province's capital city, where one administrative region was located, be upheld by one of those two options?

Not the best expert, but the best swordsman.

Of course, for a Master, a worn-out, shabby Cheonggang Sword was much more stylish than a renowned sword.

It would truly look amazing.

But a fight between Masters was often decided in an instant.

The fight between Qing and Mun Jeongyeok was just like that.

If he had known of the Demonic Arts of the ominous witch, he could have coped. But he didn't, resulting in one opening.

His dantian was severely hit by the White Hand Demonic Arts, causing his Qi and blood to become twisted and the flow of his Qi to scatter. His protective energy was broken, so he could not block the hand blade that penetrated his head, ultimately splitting it in two.

As such, in a fight between Masters, a single mistake led to defeat and furthermore, death. As a result, the higher one's level of mastery, the better their weapon had to be.

A craftsman does not blame their tools, but this saying only applied when the desired outcome was of an ordinary level.

To create a masterpiece, one needed tools suitable for a masterpiece. Thus, the more skilled the craftsman, the more carefully they must select their tools.

And now, the masterpiece among masterpieces made with the utmost devotion of a craftsman, the Paryu Sword, would meet its new owner.

"Wow. The color is just amazing."

Qing picked up the sword and gently shook it.

As the blade bent like a willow branch, Qing gripped the hilt of the sword and exerted her strength to its limit.

The sharp and sensitive sensation felt as if she could hear the blade's scream.

Aaaagh, stop, I surrender, I surrender, my bones, my bones are breaking! Have mercy on this sword! This bitch is holding a renowned sword! It's gonna break, it's gonna breeeeak!

The Paryu Sword bent to its limit, only straightening just before it seemed to break.

It had truly met a terrible owner.

While Qing was contentedly holding the Moonlight Sword (No. 11) and pulling the scabbard from Mun Jeongyeok's corpse…

"Noo!! Senior Sister! You have defeated Mun Jeongyeok!! That is incredible!!"

After separating the scabbard from the corpse, Qing rummaged through his inner pockets and asked.

"Huh? Was he someone famous?"

"Of course! If you say Mun Jeongyeok, it's the Best Sword of Bokju! If you say the Best Sword of Bokju, it's Mun Jeongyeok! He is a very famous Master of swordsmanship!!"

"Hmm. Is that so? Ah. Wound medicine. I knew it."

Since the sword seemed impressive, the spoils of war were bound to be good as well. The box alone already seemed to that part.

The wound medicine Tang Nana had given her was mostly used on Hag Yan and the rest had been eaten by her own waist.

"That is indeed so!! Soon, the Unrestrained Realm! He was a sword expert who was said to be just about to reach the Unrestrained Realm!!"

Unaram's fuss was something she had heard all the time, so it was nothing new.

However, her shouts spread far and wide.

"The Heavenly Flower Sword defeated the Best Sword of Fuzhou?"

"They must have fought in the midst of the enemy. Does that even make sense?"

"The Heavenly Flower Sword is a heroine who captured the Flame Demon Warlord even when she was at the Peak Realm. And she is the owner of a Divine Art."

It was the murmuring of Qing's rising fame.

For reference, Fuzhou was the capital of Fujian Province, and it was one of the large cities where the population of Nanning and Guilin combined did not even reach that of one Bokju.

Thus, the Best Sword of Fuzhou was far from just a neighborhood figure.

Of course, the best expert in Fuzhou was a dao user and the second and third ranked were also dao users, so Mun Jeongyeok was only the fourth.

However, he was not the Best Expert of Fuzhou, but the Best Sword of Fuzhou, so it wasn't exactly a lie.

Afterward, the government troops swarmed in and captured everyone except for the innocent martial arts instructors, thus ending the battle.

It was a victory.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Yeom Bangju, Yo Hwancheol, murmured in despair.

"How could the authorities, of all things……"

Yo Hwancheol was handcuffed behind his back.

The rope that continued from it wrapped around the neck of the person behind him.

Like that, they were tied together, forming two long lines.

If anyone tried to escape, the structure tightened the rope around their neck.

And the person behind Yo Hwancheol was none other than the Invincible
Strategist, Jo Gwangang.

"I do not know either. They even mobilized the military."

Even in the primitive, uncivilized ancient China, there was a surprisingly established system of separation of powers.

However, this did not stem from a people-oriented ideology that the
abuse of concentrated power could harm the lives of ordinary people.

It was purely a division for the convenience of the rulers, making it easier for the Emperor to rule by having his subordinates bicker among
themselves.

Of course, since the three would usually form sworn brotherhoods and shout ‘Are we not brothers?!', taking everything for themselves, the common people were always troubled.

Thus, the Civil Administration Department handled the administration of a province.

The Regional Military Commission handled the military of a province.

The Censorate handled law enforcement.

The constables were under the jurisdiction of the Censorate and the
military was under the jurisdiction of the Regional Military Commission. For the two to be in one place, the authority of the Civil Administration Department was required.

And in Nanning Prefecture, there was only one person who could make such a trinity possible.

The Prince of Xushi.

"Bangju, have you ever offended the Prince?"

"How could that be! How could a mere head of a salt merchant guild do such a thing?"

"Hmm. But how could this be? It's as if they've decided to round up all of us bastards of the Evil Factions and drag us away?"

"Could it be because of you?"

"What do you mean by that?"

"The Prince of Sichuan is staying at the Guilin Sword School, but where are the Guilin guys right now? The Iron Fist of Bailian is a guest, so what would he think if the host's household suddenly emptied out?"

"So the Guilin bastards should have been captured-"

"Who's going to be the one to complain? Will an esteemed figure try to understand the ways of Wulin?"

At that, the complexion of the former Iron Fist of Bailian, now Invincible Strategist Jo Gwangang, darkened.

"No, so you're saying this is my fault? If you could have predicted this, why did you only say so now?"

Jo Gwangang's voice sharpened, causing Yo Hwancheol to flinch.

Still, he couldn't just take the blame for something like this.

No, especially because of a situation like this.

"No, I'm just saying that as an analysis, this seems to be the logic behind it. It's my opinion. I'm not blaming you, Danju."

"Hmph. Well, it might be better this way."

"Better?"

"We might have suffered heavy losses due to a brief retreat, but how long will we be locked up in prison? It's safer inside, so wouldn't it be better to just endure a bit of discomfort and get out?"

"Ooh, what you say is."

"A man's revenge is never too late, even after some time. Once I get out, I'll request a Zenith-grade combat unit from the Alliance-"

Slap.

The rope slapped Jo Gwangang's mouth.

"These things! Talking like prisoners who have already given up on life! Do you think the constables are so easy to deal with?!"

Jo Gwangang's expression turned sour.

It was only natural since some bastard who wasn't even worth a single fist dared to strike an expert on the lips.

With the rope around his neck and the wooden shackles on his arms, he could break free if he wanted to.

However, taking revenge now was one thing, but treason was forever.

"You bastard! Squinting your eyes! What are you answering!"

"……I apologize."

"Is a mosquito crawling in? Louder!"

Slap. The brazen constable hit a Transcendent Realm Master's cheek with a rope again.

Jo Gwangang's blood pressure soared.

Then, the rope slapped him again.

It didn't hurt, but it was disgusting.

"I'll ask the General to execute you immediately-"

"No! I apologize!"

Startled, Jo Gwangang raised his voice.

"One more time!"

"I apologize!"

"Tsk. What's the point of being an expert if you're just a lowly thug who sucks the blood of commoners."

Jo Gwangang clenched his teeth until they nearly shattered.

Not only was the remark about being a lowly thug insulting, but it was also infuriating to hear that he sucked the blood of commoners from the government's lackeys, who were the very best at doing so.

I will never let that bastard go.

Jo Gwangang kept glancing back, as if to memorize the constable's face.

In front of and behind him, a long line of Sapa bastards were being dragged along in ropes.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A victory banquet was held at the Zhangshan Martial Hall.

There were casualties in the battle, but traditionally, victories were celebrated before mourning those who had passed away.

"Great Hero! May I offer you a drink!?"

"Heavenly Flower Sword! Please accept this one!"

"I must offer a drink to the new Best Sword of Bokju!"

Qing did not refuse any incoming drinks.

After all, there was nothing wrong with drinking to one's heart's content.

"Cheers! This is great! Come on, everyone! I don't know about Bokju, but let's determine who the best drinker in Nanning is today! Bring the alcohol!"

"Oooh!"

But what is alcohol?

Alcohol damages the brain, rots the liver, and destroys the five senses of sight, hearing, smell, taste, and touch, while also causing mental illness. It is a deadly poison that only feels good for a moment when consumed.

Alcoholics make the absurd claim that a glass of alcohol with a meal is good for health, but in reality, alcohol is a harmful substance that provides not a single positive function to the human body.

As such, the Orthodox Faction martial artists, who had fallen for the sinister scheme of a vicious witch, were drinking poison themselves.

They drank and drank and drank, collapsing one by one.

Thus, as the night deepened, a truly gruesome sight unfolded in the Zhangshan Martial Hall.

Unaram, who had fallen to her right knee, and Nayang Gyeol, who had fallen to her left knee. And in the front yard of the martial hall, countless Orthodox Faction martial artists were sprawled out, groaning and twitching.

Amidst this, Qing was alone, tilting her cup before filling it again, watching the droplets fall, drip, drip.

"Ah shit. I'm out of alcohol. Hey, auntie! One more bottle of hard liquor, please!"

However, it was not an auntie who approached, but an uncle. And not even a house uncle, but a guest uncle. A servant of the Guilin Sword School.

"This is a letter I was told to deliver to you, Young Lady."

Qing accepted the red envelope, and the servant hesitated, not leaving.

"Ah, right. You came all the way here. Would you like a drink? I'd like to pour you a new one, but this is the last, so, just a moment, okay?"

Qing pulled up her sleeve and wiped the rim of her cup until it squeaked.

"It's not that, it's, uh, well, several of the same letters keep coming, but the guy is not good-looking, so I thought the Young Lady should know. To think he dares to hit on the Young Lady without knowing his place? Just say the word, and next time he comes, I'll slap him across the face."

Without even a confession, the poor messenger was about to get slapped!

But it wasn't that the servant was being rude. Rather, he was being loyal.

Seeing through the veil, Qing smiled bashfully and dissuaded him.

"Ah. There's a sender, and I have no interest, so don't worry about it. Here. Since you've come, there's a lot of leftover food, so pack some up for the workers."

"Would that be alright?"

"Sure. Who's going to eat all that when everyone's knocked out? The banquet food is all that's left. Just wrap it in a cloth and return it later after washing."

"To think you would even consider the servants……"

The servant was moved, his face a mix of excitement and gratitude as he gathered the remaining dishes from the banquet.

For the servants of the Guilin Sword School, it was food given to them by a fairy! As such, praise for the Heavenly Flower Sword was expected to continue today.

Since she always addressed them with honorifics and treated them with respect, the servants regarded Ximen Qing as a heavenly fairy.

After spending someone else's food, Qing tore open the letter.

\begin{quotation}
	「I'm waiting at the Lotus Room of the Dragon Palace Pavilion.」
\end{quotation}

For now, she threw the letter into the brazier and pondered for a moment.

Should I go?

Well, they said there was no more White Snake Toxin or Black Snake Toxin, whatever it was. They said it was one of the Ten Great Poisons Under Heaven or something like that.

But since there was no time written, it meant they would wait until she came. Furthermore, there was no usual threat about one's identity attached as a postscript, so it didn't seem particularly hostile.

It wouldn't be a trap since the Sapa bastards had already been rounded up, and how could they set a trap without knowing when she would come?

Come to think of it, why wasn't that old man in the battle?

Even though the government troops sided with them, resulting in the same outcome, if there was a poison expert, they could have caused significant damage since such experts specialized in mass slaughter of weaker foes.

Did that Yeom Bangju give up on him because he was being a whiny bitch?

Qing thought for a moment.

Hmm. Then I should go right now.

It was right after they had won the battle, and since all the big shots had been captured by the officials, it would be difficult to mobilize personnel right away.

Also, they wouldn't expect her to come so soon, so it was better to go immediately and hear what they had to say rather than giving them time to loiter.

Bo Yeol's determined expression, serious eyes, and solemn voice spoke.

"This old man plans to devote himself to the Blood Cult."

Ah shit. I shouldn't have come.

Qing regretted it immediately.

This old man has gone senile.

If he wanted to join the Blood Cult, he could have just gone quietly. Why did he have to call me here to tell me this?

Does he want me to cheer him on or something? 