\chapter{Let's Have Some Fun (5)}

A true warrior should not hesitate when retreating.

This is because retreat is merely an act that promises a better future, enduring the ridicule of the present to build up strength and seek revenge.

Therefore, it is never an escape or a flight.

It is not running away with your back turned to the enemy, but a hopeful march towards a better tomorrow!

"Retreat! Retreat!"

"It's the retreat signal! Let's go!"

"Scatter in all directions and gather at Yeom Fort!"

Here, the difference between the White Tiger Team and the Black Tiger Team, the two White-Grade Combat Teams of the White Bear Squad, and the Black-Grade Combat Team of the Black Bear Squad was revealed.

Unlike the bewildered Black Bear Squad's members who were caught by the enemy, the White-Grade Combat Teams immediately scattered in all directions as if saying, ‘Oh, we've been waiting for this! Charge! In the opposite direction of the front!'.

"The enemy is fleeing! Catch them and kill them! If we let them live, they will be a source of trouble in the future!"

Gang Suyang, who was also well aware of this aspect of the Unorthodox Faction, their petty inability to forget grudges, immediately shouted to inform them of the situation.

"Waaaaah!!"

With that, the morale of the Orthodox martial artists surged.

It goes without saying, but if one had to wield a sword and slash, it was much easier to face the back than the front.

This was because human eyes could not see behind them and joints could not exert force backward.

Therefore, one could just stab away without worrying about any counterattacks.

A strange glint flickered in Qing's eyes.

At first glance, it seemed red, but upon closer inspection, it was not just red but also blue, the color of a blazing fire in lush greenery, the color of twisted blood, a beach filled with the corpses of thousands, tens of thousands of fish, and the lifeless sheen emanating from the eyes of a dead fish staring blankly at the sky.

Despite the ominous glint in her eyes, her lips were wide open, revealing neat and tidy teeth.

And so, she slashed and slashed again. Ah. Where are you running off to?

Then suddenly, Qing thought that the retreating back of the Unorthodox martial artist looked very familiar.

Suddenly, Qing was standing somewhere.

A world drawn only with black and white outlines. Is this a market? A familiar back that boldly stepped on the vegetables that had spilled out onto the ground and an old woman wailing as she flailed her arms and legs. ‘Just kill me, just kill me, you bastard. Do you not have parents? How can you do this to me?' she cried.

Then, an enraged scabbard struck the old woman's head harshly.

The old body collapsed among the scattered vegetables, bright red blood flowing from her head in a black and white world.

The crimson blood touched the market floor and moved in a strange manner, splitting, bending, twisting, meeting, and intersecting, until it finally took the shape of letters that people called numbers.

One hundred and seventy-two.

The back of the person below, the fleeing figure with its tail between its legs looked somehow very familiar. It had a familiar vibe.

"Huh."

Qing's head tilted at the ambiguous sense of deja vu.

Why does it seem like I've seen that somewhere before?

Well, the backs of fleeing bastards all look the same. After all, I can't see the faces of those who are running away.

Qing swung her straight sword broadly.

The blade entered from outside the thigh and exited from the other side of the thigh.

The legless torso of the old woman, no, the Unorthodox martial artist, tumbled to the ground.

Qing paused again.

What was that? Something just flashed by?

But just as she tried to recall, it felt like a dream that had already passed. Although she knew she had dreamed, she could not remember the details, leaving only a vague and uneasy feeling.

Something…… Qing extended her mind, trying to grasp the fading dream.

Yes, there was definitely a scene I saw. It was-

-Pee-pee-peep! Pee-pee-pee!

At that moment, a loud whistle pierced her ears!

The elusive ‘something' that was just within reach shattered in an instant and Qing's eyes flared up in flames!

"Which fucker is it this time."

Qing had a very, very, very strong aversion to signal pipes.

How dare you blow a pipe during a sacred battle?

And if you're going to blow it, at least blow it well!

Noise pollution! Absolutely unforgivable!

Thus, Qing suddenly accelerated.

"Young Lady!"

The 창(chang) woman desperately shouted and tried to chase after her, but 각다귀(gakdagwi) grabbed her by the hair and stopped her.

"You fucker, how dare you grab a woman's hair-"

"Let her go. It's all over for them anyway, so there won't be any danger. Just let her enjoy herself."

"What are you talking about? Enjoy what? Do you think Her Eminence is some kind of murderer who delights in slaughtering people? Are you trying to get me in trouble with Yeon Pa?"

"Yeon Pa also, ugh, never mind. You're a woman, but you're really clueless, huh. Sigh. Whatever. Never mind."

Gakdagwi shook his head.

The chang woman's expression turned grim.

Regardless, Qing ran.

Since the Unorthodox martial artists were also running, no one was there to block Qing.

But someone was running shoulder to shoulder with her, so she looked to the side and saw an Unorthodox martial artist.

Hmm, 99 Points. Ah, shit. One point short.

Qing jabbed the side of the Unorthodox martial artist with the hilt of her sword.

After sending the grunting bastard tumbling to the ground, she focused on the one blowing the whistle. That fucker, that fucker is unforgivable.

I'm going to kill all those who blow on reed pipes.

And finally, Qing's figure stretched out long and a shout full of irritation rang out.

"Shut up! Stop making that damn whistling noise!"

Moon Jeongyeok, who was continuously sending retreat signals, was startled by the sudden shout and raised his sword.

Clang! The blades collided and sparks flew.

"You are-"

"Public! Places! Be quiet! Please!"

Clang! Clang! Clang! Clang! With each word, sparks flew once and Moon Jeongyeok was pushed back one step.

With each step back, Moon Jeongyeok's expression gradually became more serious.

What is with this wench's strength?! It was a desperate expression that suppressed the urge to scream.

There was no technique in her straightforward trajectory, but the force contained within was a ton of solid pressure.

A skilled swordsman was proficient in the art of softly deflecting attacks and creating openings.

However, it was said that four ounces could move a thousand pounds. But when a wheel rolls, tilting the sword against it won't change the carriage's direction.

The sword would just break or the person holding the sword would be thrown off.

Instead of deflecting Qing's trajectory, Moon Jeongyeok's sword was being pushed back.

So what else could he do other than take a step back to avoid it?

"Wait! I am Moon Jeongyeok-"

"Moon Jeong? Then I'm the North Capital Station, you bastard!"

Clang! Clang! Clang!

Moon Jeongyeok could not understand Qing's anger.

What's going on? Why is she so angry? Did I perhaps unknowingly do something to offend the Heavenly Blossom Sword?

But the life of a martial artist was such that grudges could be formed in unknown places.

Perhaps he had slain one of the Heavenly Blossom Sword's acquaintances.

Of course, it was just the sound of the signal whistle that had sparked Qing's anger, but no matter how imaginative a martial artist was, there was no way they could think of such a reason.

"Gal! How dare you speak like that to a senior of the Sword Path!"

"Heh. Senior my ass. I've never had an Unorthodox piece of shit as a senior. Those who don't give anything but expect to be treated with respect are the ones always harping on about being seniors."

"What?"

"Now then, it's time for you to go! Moonlight Sword, no, Hell, no, yeah, 참(cham/true) Sword! That's it, it suits the Cham Sword perfectly!"

Qing, who had suddenly given a fitting name to her beloved, oversized cleaver, smiled in satisfaction.

"Go forth, Cham Sword!"

Moon Jeongyeok saw Qing's waist twist sharply.

Her right shoulder turned in a bizarre manner.

So much so that he wondered how a human joint could do that. Her right hand, holding the straight sword, peeked out from beyond her left shoulder.

No matter how flexible she was, that was one thing. But wasn't she just putting on airs, twisting her entire body to prepare for a strike?

Moon Jeongyeok placed his left hand on the blade of his sword and held it at an angle.

And then, clang!! An intense collision.

"Huh. Cham Sword?"

The blade snapped, leaving only an inch above the hilt of what was once Cham Sword.

If Cham Sword had a consciousness, it would have said, ‘What? This sword is? My beloved?' and the original owner of the straight sword, who was now in the afterlife, would have said, ‘That's a total robber bitch'.

However, weapons do not have words and the dead have even fewer.

"Hmph! Even after losing your weapon, you're still so full of yourself!"

Moon Jeongyeok's eyes sparkled.

An opportunity! A swordsman had lost their sword, so, hmm? A swordsman? Why is a swordsman using a straight sword as their beloved weapon? Why?

Suddenly, doubts surged in Moon Jeongyeok's mind, causing the tip of his sword to shake ever so slightly.

However, whether it shook or not wouldn't have made much of a difference.

This was because the Heavenly Blossom Sword, who had lost her weapon, instinctively reached for her right palm to grab the sword.

To think that a genius of the ages would be flustered by the loss of a hand.

If you're going to lose a hand, you should lose the left one. As Moon Jeongyeok smiled faintly…

Clang!

Clang? Moon Jeongyeok's face turned blank.

After all, even a Late Stage Transcendent Realm couldn't catch a sword swung with Sword Force with their bare hands, even if they had used Force Compression.

At that moment, Qing's left hand struck Moon Jeongyeok's abdomen.

Moon Jeongyeok's body flew backward in the shape of the letter ‘V'.

What was the reason that Moon Jeongyeok's mind suddenly recalled the wrinkled face of Sa Sa'ui, along with the expression of being on the verge of death due to frustration and injustice?

‘That Heavenly Blossom Sword wench is a White Hand Demon, I tell you! She really is! She really is a White Hand Demon! For real! I'm being serious!!'

Ah.

Moon Jeongyeok finally realized.

No, how can that be true? That doesn't even make sense.

Moon Jeongyeok was wronged.

But he had no time to feel wronged.

The Heavenly Blossom Sword was rapidly approaching.

The pale, elongated fingers, indeed the most beautiful hands in the world.

Suddenly, the flickering flames beyond the veil, the cursed Demonic Art's side effect that those in the know called the Wheel of Transmigration.

"Why are you really a Transmigrat-"

Moon Jeongyeok's words ended there.

This was because Moon Jeongyeok did not cultivate the tenacity to keep talking even after having his head pierced with a hand.

If he had such tenacity, he might have survived with a piece of metal embedded in his head, leisurely reminiscing about the good old days while smoking a rolled cigarette.

This is why people should cultivate tenacity.

Moon Jeongyeok, the First Sword of Bokju. His head split and he died.

The more skilled and experienced martial artists were the first to flee.

They were smart older brothers who threw their younger siblings to the wolves in order to survive.

But even as they escaped, they noticed an unfamiliar wall suddenly wriggling on the main road. By the time they arrived, they realized it wasn't a wall but a barrier of shields.

"Stop! How dare you violate the law of the nation and brandish weapons, you wicked criminals!"

Spears protruded from the gaps between the shield wall.

In fact, it wasn't hard for people of Zhongyuan to infer that archers were lined up behind them.

Why are the government bastards suddenly here?

"Esteemed Sir, we are martial artists of the Mur-"

"Shut up! Do you think martial artists are not citizens of this nation?! Can you not immediately discard your weapons and kneel!"

"Esteemed Sir, the government and Wulin are-"

"You bastards! Open fire!"

The general cut off the Unorthodox martial artist's words and gave the order, revealing the muzzles of the cannons as the shield wall split to the left and right.

The people of Zhongyuan in this era had a habit of suddenly turning into docile lambs in front of cannons.

After all, thousands of extremely sharp pieces of metal would fly out of those muzzles.

It was said that one would need to stand behind at least two people for the third person to barely survive the power of those metal fragments.

"We'll kneel! We'll kneel!"

The Unorthodox martial artists threw away their weapons and knelt on the ground.

And then, a beat later, the pursuing forces of the Orthodox Faction arrived.

The sight of the bastards who had suddenly knelt was surprising, but what was even more astonishing was the array of cannons aiming at them.

The Orthodox martial artists, as they arrived, froze and obediently sheathed their swords.

"What are you?"

"Esteemed Sir, we are martial artists of the Gyerim Sword Sect……"

"Ah. His Highness mentioned you. You are the virtuous martial arts instructors. It seems that a wicked group attacked the martial arts dojo, so we came to arrest them. You may now relax and return."

The expressions of the Unorthodox martial artists turned to shit.

Some were called wicked criminals, while others were called virtuous martial arts instructors!

"Uh. Um. Thank you for your hard work."

The Orthodox martial artists awkwardly bowed their heads.

They didn't know why the government was taking their side, but shouldn't they at least retreat in front of cannons?