\chapter{Let's Have Some Fun (4)}

Boyeol was in the smoke.

He was trapped in a rather thick cloud of smoke.

"Damn it, how much did they burn for it to be this thick. My throat feels all stuffy."

Boyeol was an expert of the Early Stage Unrestrained Realm.

However, those who used Poison Arts were usually considered a level below their actual realm.

This was because the higher one's realm, the less effective poison became.

Besides, look at this. An expert of the Early Stage Unrestrained Realm was merely imprisoned in such a crude cell, with only the smoke of the Sansaghyang1 to keep him subdued.

However, since it was a type of poison that caused the dantian to explode if the Inner Qi was dispersed, these measures were enough to keep him obediently imprisoned as he focused on controlling his inner turmoil.

Then…

A figure vaguely appeared in the smoke before revealing itself.

"Elder, are you alright?"

"You… Aren't you the third child of the Yo family? What was your name again? Yomin?"

"Yes, I am Yomin."

Boyeol's mind cleared.

My evidence! My evidence is here!

"Your cheek, is your cheek alright? Come closer, let me see."

At that, Yomin approached the bars.

Boyeol grabbed his chin, turned it left and right, examined it, tapped it a few times, asked if it hurt or not, if it pulled or not, and checked his pulse with a sense of urgency.

And the result?

"It's all healed. It's completely healed."

It was truly all healed!

Since he had been hit in the cheek by the White Hand Demonic Arts, his cheeks should have been rotting by now, with his teeth visible through the decaying flesh. But not only was that not the case, his skin even seemed to have become smoother and better.

My evidence!

Boyeol's vision went dark.

Regardless, Yomin asked.

"I-I brought some incense. Would this be able to replace the smoke of the Sansaghyang?"

"Wait, are you trying to help me?"

"Yes……"

"Why? Did Yeom Bangju order you to?"

"It's not that. I just wanted to thank you for checking my pulse earlier……"

Boyeol felt like he had been hit in the back of his head.

It was just the usual whim of an old man that popped up every now and then.

Seeing a pitiful kid being beaten by his father, he had checked the wound and found traces of the White Hand Demonic Arts. Knowing that the flesh would rot away anyway, he gave him a jar of Wound Ointment, hoping to at least preserve a bit more of his cheek.

However, it seemed that this was enough to warm the heart of a neglected child who was mistreated by his father and bullied by his brothers.

Under Boyeol's instructions, Yomin opened the lid of the brazier, replaced the contents, and lit incense sticks, placing them discreetly in the back.

Now, the thick smoke of the Sansaghyang would gradually subside, and a different kind of smoke would provide a distraction.

Escaping would not be difficult once the Sansaghyang was cleared out.

Once his Inner Qi recovered enough to use Sword Force, he could just cut through the bars and leave.

"W-Well then, I shall take my leave now……"

"Wait, how did you get in here? Weren't there guards in front?"

"Yes. But there is a passage."

"Hm. Hey, kid."

Boyeol scratched his wrinkled cheek.

"I was going to keep my mouth shut since it's not my place to interfere in other people's family matters, but since you've shown me such kindness, I have to tell you. Your father originally intended for you to die. The guys from the Gyerim Sword School were going to kill you, and he was going to use that as an excuse to attack, regardless of any deadline."

At that, Yomin's eyes widened, and tears welled up.

"But, I, what did I do to deserve that."

"If you stay in the clan, you won't live long anyway. Do you think the guy who wants to establish a noble clan will let a useless branch family live? So you should leave immediately, but I'm already over eighty, so I was thinking I needed someone to take care of me."

At that, Yomin's red eyes widened.

Telling him to take care of him meant the same thing as telling him to become a disciple.

"Me, me? But I have no talent in martial arts……"

"Originally, those without talent are the ones who should learn Poison Arts. If you can consistently expose yourself to poison, you'll be able to do your part. And even if that's not the case, Poison Arts often overlap with medical arts, so you'll be able to make a living."

Yomin hesitantly joined his hands.

Boyeol hurriedly stopped him.

"Think about it. This old man has nowhere else to go, so I'm thinking of joining the Blood Cult. You saw an innocent person being called a spy of the Blood Cult, so fine, I'll really become a spy of the Blood Cult. But you're still young. So if you want to join those bastards of the Blood Cult, come with me. If not, then let's pretend we didn't see each other today."

The Blood Cult.

At the heavy and ominous words, Yomin gulped.

"They say the Blood Cult only eats human flesh……"

"Are there any people who only eat human flesh? Besides, even those guys are human. They'll eat what tastes good. I know a kid from the Blood Cult and he's actually better than those Unorthodox Faction bastards. He knows how to respect his elders too. Come to think of it, I guess there are people with their own stories even among the trash of the Blood Cult."

If the kid from the Blood Cult, Qing, had heard that, she would have asked back, ‘Eh? Me?'.

"Still, the rumors are not unfounded. Most of them can be considered trash. So if you like the idea of being among such bastards, follow me. If not, let's go our separate ways here."

At that, Yomin hesitated for a long time, but soon his eyes became a bit more resolute.

Yomin took his stance once again.

"I know I'm a worthless fool. My martial arts are lacking, and I have no particular skills, so I have no confidence to make a living anywhere. But since you said you would take me in, I will serve you for the rest of my life."

"Good. Doctors are not treated poorly anywhere. Even the Blood Cult bastards are human, so they wouldn't treat a physician who can heal them badly. I don't have a sect, so we'll just skip the formalities with a single bow."

With that, Yomin prostrated himself on the floor.

Boyeol, who was happily looking at his first disciple, suddenly clenched his teeth.

"But… Before we go, shouldn't we give these bastards a good spanking? What was it with that advice? He's barely a kid and I'm older than his own father."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's Qinggong was unparalleled.

This was acknowledged by both the Zenith Among Women and the Divine Thief, making it a skill worthy of recognition throughout Wulin.

With the explosive acceleration of the Celestial Demon's Dominating Step that reached maximum speed in just three steps, the Mid-Air Dash that was the fastest Qinggong in short to mid-range, and the Thousand Li Flight that lived up to its name in long-distance travel.

Furthermore, she could also use the Yue Maiden's Mountain Walk, a gravity-defying footwork that allowed for extraordinary changes in movement, as well as the Ethereal Escape and Subtle Steps for emergency escapes.

Therefore, even if Qing suddenly plunged into the midst of enemies in a fit of bloodlust, she had the ability to immediately retreat if she realized it was too much.

However, that was usually not the case for most people.

If one were to dive alone into enemy lines, they had to at least die after performing some heroic feat to receive a barely honorable funeral.

Otherwise, it was just a dog's death.

This was also why commanders always emphasized formation and discipline in battles.

As soon as Qing confirmed that he had returned safely, the three guests breathed a sigh of relief. But then, something felt off.

"Old Man Gyeon!" "Grandpa Old Dog!" "Gyeon No!"

The female warrior, the horsefly, and the illiterate poet exclaimed.

At that, Qing became triumphant.

"Let's go save him!"

"Young Lady!" "Young Lady!" "Young Lady!"

As Qing charged forward again, the three Transcendent Realm guests hurriedly rushed to stand shoulder-to-shoulder.

Could mere First-Rate martial artists block the path of four Transcendent Realm experts?

The four broke through the enemies with overwhelming force.

"Ack, Bear-thing. Me too, Kwek."

It was when Nayanggyeol, who was trying to follow behind, was grabbed by the scruff of his neck by one of the Royal Household's guests and lifted into the air with his two feet dangling.

"Young Lady, you stay with us. You can't go wherever you please. It's hard to keep up with you when you're squeezed between Transcendent Realm experts."

"Ah shit, I'm so sick of this Transcendent this, Transcendent that."

Meanwhile, Old Man Gyeon was fighting well.

His peculiar dual weapons, a spear in his left hand and a sword in his right, were respectively called the Sangsan Spear and Sangsan Sword.

As the spear and sword drew straight lines, his two arms spread out like a fan.

The Unorthodox Faction's martial artists grabbed their chests and collapsed to the ground.

Although the spear tip and sword edge pierced their bodies, the holes that were made were only as small as pinpricks.

It was a vicious technique that precisely targeted vital points and pulled back, causing one to die in agony.

The Unorthodox Faction martial artists, who had rushed in after hearing the commotion, hesitated and created an empty space around Old Man Gyeon.

The Unorthodox Faction martial artists lying between Old Man Gyeon and his enemies grasped the tiny holes in their chests, writhing in an attempt to survive.

They were members of the White Bear Squad.

Since Jo Gwang-ang, who liked to pretend he was well-versed in military tactics, had organized his troops in formation, he naturally positioned his own men in the rear where there was the least risk.

So how could Jo Gwang-ang just stand by and watch as his subordinates were being killed?

A Transcendent Realm expert, huh? Though he was still young, he had to be taught just how big the difference between each small step was once one reached the Transcendent Realm.

Thus, Jo Gwang-ang appeared, shouting fiercely and boldly.

"How dare you harm the warriors of the Four Dao Alliance! You wench, uh, who are you, you old codger!?"

He had seen the Heavenly Flower Sword fall earlier, but when he rushed in, the Heavenly Flower Sword was nowhere to be seen, and there was only an old man.

Groan. His subordinates were crawling on the ground, clutching their necks and chests. However, the bleeding didn't seem too severe.

It seemed like there was still a chance to save them, even though they would definitely die since their hearts had been pierced.

As such, Jo Gwang-ang's mind was put at ease.

Jo Gwang-ang kicked off the ground, shouting and raising his fighting spirit.

"Alright! Old man! Today is your funeral!"

Old Man Gyeon responded by raising the tip of his spear.

And then, a brilliant light bloomed on the back of his hand holding the spear, forming a flat, wide terrestrial star.

It was Force Compression.

Jo Gwang-ang demonstrated a wondrous feat of retreating at the same speed as he had been advancing.

Screeeech. It wasn't the actual sound, but rather a sound that could be heard with the eyes, a sound that could be seen with the eyes.

After all, for the Unorthodox Faction, the strong were those with power!

Retreating from the strong was never a shameful act!

"Y-You hid a Master! You despicable bastards! Is this what it means to be part of the Orthodox Faction?! Shouldn't we fight fair and square, after laying our cards on the table?!"

One had to wonder what the members of the Unorthodox Faction thought of the martial artists of the Orthodox Faction.

Jo Gwang-ang's face was drenched in thick beads of sweat.

Hiding one's hand! I was so perfectly fooled!

However, Jo Gwang-ang was also a self-proclaimed expert who had read dozens of military strategy books and memorized them all.

His brain, pushed into a corner, heated up and worked diligently to come up with the best possible plan.

"Strike! Warriors of the White Bear! The enemy is one, we are many! Unleash the Infinite Billowing Waves!"

Infinite Billowing Waves. It meant an infinite number of massive waves, and it was the most basic formation used to face a large number of enemies with just one.

"Kill!!" "We are the White Bear!" "Warriors of the Four Dao Alliance, stand firm in your positions!"

A very ominous cry was mixed in, causing Old Man Gyeon's expression to contort.

These Unorthodox Faction bastards are insane!

He thought he should first pierce the heart of that bastard in charge, but then, Old Man Gyeon's expression turned blank.

This was because among the Unorthodox Faction martial artists who were moving left and right to take their positions in the formation, the ones who seemed to have the swiftest footwork suddenly turned around and ran away.

The leader, Jo Gwang-ang, was the same.

Jo Gwang-ang's brain faithfully produced a plan.

The Thirty-Sixth Stratagem among the Thirty-Six Stratagems, Running Away Is The Best Option!

If it looks like you can't win, don't hesitate to run!

It was common knowledge that if an order that everyone knew was given, the enemy would obviously be prepared.

To the elites of the White Bear Squad, Infinite Billowing Waves did not mean to form a formation.

It meant that it was hopeless, so throw away your underlings and run.

Jo Gwang-ang immediately broke through the combat unit and rushed toward Moon Jeongyeok.

"We've been had! We must escape immediately!"

"What are you talking about! Suddenly-"

"There was a hidden expert! An expert of the Unrestrained Realm was hiding!"

At that, Moon Jeongyeok's expression became serious.

"An Unrestrained Realm expert alone, the three of us can-"

"Who's going to deal with Gang Suyang!? What about that Ximen Qing bitch!?"

"If the Transcendent Realm experts form a formation-"

At that, Jo Gwang-ang pounded his chest.

"Then who's going to deal with their Transcendent Realm experts!"

"We can use First-Rate martial artists from the combat unit-"

"Are you going to plug a hole by creating another one! Are you planning to go down to the Third-Rate? Are you trying to get the combat unit annihilated! We have to save those who can be saved!"

Such a swift and decisive Thirty-Sixth Stratagem.

In fact, Jo Gwang-ang's judgment was exemplary for a commander, so it could be said that he wasn't just a guy who read military strategy books for nothing.

If a battle was unwinnable, one had to stop immediately and retreat, no matter the losses.

How many commanders in the past and the future had failed to escape a losing battle because they were fixated on the losses, ultimately ruining everything?

Beep beep!

Finally, Moon Jeongyeok sent the signal to retreat. 