\chapter{Let's Have Some Fun (7)}

Qing's eyes narrowed into slits.

After eating well, drinking well, and being about to sleep well, she was suddenly being told that he was going to join the Blood Cult?

What is this? Is he showing off? Or has he gone senile?

Or does he just want to die?

"Joining the Blood Cult isn't necessarily a bad thing, is it? I'm one of the top ten poison masters in the world when it comes to snake venom, and while my medical skills might not be exceptional, how many doctors with martial arts are there?"

"It's getting worse and worse. So?"

"Mm. Yes. Well, if I'm going to join the Blood Cult, do I need to prove anything? Would they just believe me if I said I'd join the Blood Cult now?"

"Hmm. That's true, isn't it?"

She was curious after hearing that.

The Blood Cult must have some means of verification, right?

The Blood Cult was a group that even the Orthodox Faction, the Unorthodox Faction, and even the Demonic Cult detested.

Shouldn't they have already infiltrated and had their movements revealed, leading to a joint attack by all of Wulin?

"Ahem, so, I killed the head of the Yao Family. I also burned all the records, so the Yao Family is done for. It's completely ruined."

So that's why his Evil Karma had decreased so much.

But there was a guy who bothered her more than that-

"Huh. What about him?"

Qing pointed to Yao Min, who was anxiously rolling his eyes in a corner.

As soon as the pale, slender finger pointed at him, Yao Min visibly flinched and couldn't hide his anxiety.

"Didn't you say he was the third son or something? I definitely saw him causing a disturbance in the Guilin Sword School. You said you killed the head, but?"

"I decided to make him my disciple. He's a poor fellow, shunned by his parents and bullied by his siblings. He's filled with resentment because of that. He's also someone with a venomous heart, enough to feed poison to his own siblings."

"Teacher? This disciple-"

"Oh, hush. How about it? Isn't he perfect for the Blood Cult? He's the perfect talent for the Blood Cult, almost as if he was born to join them."

As the veil was turned, Yao Min flinched.

To have survived a conflict with Qing meant that his Evil Karma was not in the triple digits.

He didn't seem like such a vicious guy, considering how he licked the ground earlier.

What does it even mean to be someone born to join the Blood Cult?

"So, what do you think?"

"Why are you trying to join the Blood Cult? You have decent medical skills."

"The Unorthodox Faction abandoned me first. They had been looking down on me for a while anyway. Yeah, they think I'm just some mediocre guy who needs to be respected."

Now he was calling the Four Great Evils 'bastards' and the Unorthodox Faction 'those guys', showing that he was truly going off the rails.

"They look down on you? They look down on an Elder?"

"Oh, don't get me started."

Sa Sasa claimed to be one of the top ten when it came to snake venom.

It was usually a bit of an empty boast to call oneself one of the top ten.

Guys who were roughly around sixth or seventh place would skip over those above them and put themselves in fifth place.

So, those who claimed to be in the top ten were usually experts who were somewhere between eighth and thirteenth place, give or take.

Moreover, Sa Sasa specified that he was in the top ten only when it came to snake venom, not even poison in general.

Boyeol knew he was ambiguous.

He was over eighty years old and had long given up on reaching the Unrestrained Realm.

Knowing he was dull-witted, he focused on snake venom, but even then, there were many well-known doctors or masters of poison arts who knew more than he did, such as the Divine Doctor, the King of Ten Thousand Poisons, or the Life-Reaping Physician.

His medical achievements were just at the level of an old doctor, and he hadn't written any medical books with his name on them.

"Well, that's true. But you're still an esteemed elder who has surpassed the age of eighty. That alone is amazing."

"That's kind of you to say. It also means I don't have much time left to live. If it weren't for you, I wouldn't even have been able to come to Nanning and see the top of the Dragon's Palace Tower. How unfortunate would that have been?"

"So you're going to the Blood Cult to take revenge?"

"More like, the living must live, well, no. Yes, revenge. I will make the world drown in blood. What is the Blood Cult's slogan? Blood something? Blood Heaven Stands?"

"Why are you asking me that? Why don't you just join the Orthodox Faction instead of the Blood Cult?"

"The Orthodox Faction won't stop personal grudges, and what if the experts of the Unorthodox Faction come one by one, using their status as an excuse?"

"Hmm. Well. I see. But why did you call me here?"

"So I need your help. Please introduce me to the Blood Cult. Huh?"

"Huh. Me?"

Qing blinked.

"Wouldn't it be a bad thing for you? I'm a master of the Unrestrained Realm, you know."

"Wait, why are you suddenly bringing up my position? You keep doing that."

It seemed to be this elder's habit to keep mentioning 'your position' and 'for your sake' whenever they met.

"Why. Isn't it common for people to be similar? Won't the Blood Cult also have factions and power struggles? So it'll be good for you to have a solid ally. Yeah. And what better way to use in a factional fight than deadly poison."

"Well, that's a big yikes, old man. Trying to use poison in a factional fight. And why are you keep asking me about the Blood Cult?"

"Well, who else am I supposed to ask about the Blood Cult if not a member of the Blood Cult?"

"Huh?"

Qing was momentarily dumbfounded, then pointed a slender finger at her throat and asked.

"The Blood Cult?"

"Yes?"

"I'm not in the Blood Cult, though?"

"What are you talking about? Aren't you the White Hand Demoness?"

"Hey, I'm not the White Hand Demoness. Just because I learned the White Hand Demonic Arts doesn't make me the White Hand Demoness, okay?"

"If you learn medicine, you're a doctor, and if you learn swordsmanship, you're a swordsman, so why isn't someone who has learned the White Hand Demonic Arts a White Hand Demoness?"

"It's not White Hand Demonic Arts, it's Divine Maiden's Divine Palm."

Now it was Boyeol's turn to be dumbfounded.

"Divine Maiden's Divine Palm?"

"Divine Maiden's Divine Palm."

"Not White Hand Demonic Arts?"

"Maybe it's a little similar? So you might be confused?"

Boyeol burst out.

"How can that make any sense!"

"Why wouldn't it make sense?"

Qing was defiant.

Boyeol was dumbfounded.

"Didn't you act like the White Hand Demoness in front of me and take the poison?"

"Ah."

Qing's moral compass spun rapidly.

Of course, the compass, worn out from the Jianghu, was almost a perfect circle and didn't really scratch her conscience.

"Hehe. Sorry."

"What!?"

"What can I do? I really wanted the Ten Great Poisons Under Heaven. I could catch one Great Demonic Adept with each bottle. If three Great Demonic Adepts disappear, how much more beautiful would the world be? It's a good deed for you too, isn't it? It'll all come back as good karma later, so, um, as you said, it's not necessarily a bad thing for you, right?"

"No, but, what. So you had no intention of keeping your promise from the start?"

"I'm sorry."

"What would you do if I revealed your identity?"

"The Heavenly Blossom Sword is actually the White Hand Demoness? Who in the world would believe that? Especially coming from an evil Demonic Adept of the Unorthodox Faction? Would you honestly believe that, Elder?"

"Still, the name of Sa Sasa is not so light. If I say that I saw it with my own eyes-"

Boyeol's words were cut short.

Black spread from Qing's fingertips, quickly crawling past her sleeves.

Then, on her pitch-black hand, purple Demonic Qi sparked and crackled.

"Now. Now that you've seen it with your own eyes, are you going to say that I also learned the Black Assassin Demon's Ultimate Skill and the Purple Lightning Demonic Arts?"

"Uh, um?"

Then Boyeol suddenly remembered something.

‘Why don't you just say that I also learned the Black Assassin Demon's Ultimate Skill, the Purple Lightning Demonic Arts, and that I have a Wheel of Samsara in my eyes?'

"Perhaps you haven't learned the Wheel of Samsara, ah. Indeed. You have. What a guy, really……"

"Now. Will people believe you if you say that?"

"Hmph. What's there not to believe?"

"Hey. If I said that Mun Jeongyeok was actually a spy for the Orthodox Faction who had learned the Tai Chi Sword, would-"

"What! That guy, Mun Jeongyeok!? No wonder! I knew it! How could he have known all that! So he was planning to eliminate me all along! That damn spy of the Orthodox Faction!"

What is with this Demonic Adept being so naive?

Well. I guess that's why he got tricked three times……

Qing sighed deeply.

"Haa. Haa."

But there was one mouth, yet two sighs.

When Qing turned her head, she saw Yomin, who had taken a deep breath, startle and hide behind his teacher.

"Th-Teacher. It seems like he was asking if you would believe it if he said Mun Jeongyeok was a spy for the Orthodox Faction, not that Mun Jeongyeok actually is a spy for the Orthodox Faction……"

"What? Ah, yes. I knew that. I was just saying. I thought it was an unbelievable story."

Didn't he look too surprised for that?

However, since she had already deceived him three times to get the poison, Qing decided to keep her mouth shut and cautiously observed the situation.

"Even though I trusted you. How could you."

"We were between the Orthodox Faction and the Unorthodox Faction. And actually, the one who was threatening was, huh. That's right. You even threatened to reveal my identity, so what's the big deal?"

"You brat!"

Boyeol jumped up and extended his fist.

A white snake's head emerged from his long sleeve, hissing as a cute threat.

Qing, not to be outdone, knocked over her chair and placed her hand on the hilt of her Paru Sword.

"Hmph. Alright, let's settle this today! I tried to go easy on you because I thought we had some kind of bond, but what does the Blood Cult even matter? You're just going to be the biggest Demonic Adept under the heavens, aren't you?"

As they glared at each other in a standoff…

Hiss, hiss. The white snake, continuously threatening, and Yomin, who had taken a step towards his teacher's right.

It meant that even if he was struck by a sword, he would be the first to take the blow.

At that, Qing let out a deep sigh.

"Anyway, you said you have nowhere to go, right? You can't go to the Orthodox Faction."

"Ahem. Well. That's right."

"Shall I introduce you to a merchant company I know? It's a small, no, it doesn't seem small anymore. It's a fairly large company now, and it wouldn't be bad for you to quietly practice medicine there."

Qing thought of Seol and Choi Leeong.

Their Evil Karma kept decreasing whenever she saw them, so they must be spending their money on good deeds. Wouldn't it be even better to have a doctor there?

"Ahem. But as I said, I have enemies. The bastards of the Unorthodox Faction will definitely try to harm me."

"There are a lot of Masters there. Like, a lot."

Not only Choi Leeong, but also some errand boys, porters, and even the middle-aged woman doing chores in the kitchen were all Masters.

They were probably escapees from the Demonic Cult. Were they Demonic Defectors? Was it too much to call them Demonic Defectors? Demonic Cult Defectors? Anyway.

Of course, all of them were very devout followers who had never defected from the Demonic Cult.

However, they were also fanatics who would say that someone had defected from the moment Qing said they had.

And if I stay at the Seolga Company, I might be able to get poison from time to time, right?

I like poison. I like it so much. It's just the best.

It's good if I eat it, and it's good if others eat it. It's just so versatile.

"Ahem. Would that be okay, though?"

"As long as you're okay with it, Elder. They all have their own stories, so they'll understand."

"Then, without any shame, I will be indebted to you."

It wasn't very dramatic, but the negotiation was settled.

Qing picked up the fallen chair, and Boyeol sat back down on the chair that Yomin had set up for him.

"Go to the city of Zigui, west of Hubei Province, and look for the Seolga Company. Tell them I sent you."

"Would just words be enough? Is there any kind of token or something?"

At that, Qing took out an iron hairpin and handed it over.

She could always get it back later when she visited the Seolga Company.

And then, Qing's eyes lit up as she spoke.

"Ah. By the way, about that snake earlier, does it bite? Can I touch it? No, I mean, even if it bites, can I still touch it? It looked so pretty."

"Oh. Of course, snakes are such gentle creatures. People who don't know think they are fierce, but they're not fierce, just sensitive. In fact, they are quite intelligent creatures……"

Boyeol's face lit up.

After all, people's faces always brighten when they talk about their favorite things.

This was why Boyeol sold snake venom.

Actually, if Qing's introduction was to be summarized…

She was just sending him to a den of Demonic Cultists, especially the hardcore ones, to suck out all the precious poison from him.

Unaware of this, Boyeol passionately talked about snakes.

After all, naive people get tricked endlessly, without limit.