\chapter{Let's Have Some Fun (2)}

The way things were going was quite unusual. Every warrior he saw had a serious expression and was busy inspecting their weapons.

It was a truly astonishing sight.

Why were these bastards suddenly acting like martial artists?

For the warriors of the Unorthodox Faction, weapons were more like an inconvenient lump of metal that they couldn't understand why they had to carry around, something that needed cleaning only when rust started to appear.

But if everyone was inspecting their weapons, it was only natural to be suspicious.

Boyeol singled out one of them.

"Hey, you. What are you doing?"

"Preparing for war, sir."

Boyeol was bewildered.

"War? What war? Are we attacking the Nanning Sword School? Is the Prince present? Are we all looking to die together or something?"

"I heard it's not the Nanning Sword School, but some small Orthodox Faction called the Jangsan Martial School."

At that, Boyeol's expression turned into a deep frown.

Why should he, a master of the Four Great Evils, learn about the war from a low-ranking warrior like this one?

Thus, Boyeol stomped angrily towards the highest-ranking guest room of the Salt Gang.

Thump, thump!

By opening the door roughly enough to almost break it, Boyeol displayed his displeasure.

It might have been considered childish, but people tend to become more childish as they age.

"The Fourth Great Evil has arrived!"

The three Unit Leaders, the Vice Unit Leader, and the Squad Leaders were already gathered in the tea room.

It seemed they had been holding an operations meeting without him.

"What in the world is this? You're going to attack the Jangsan Martial School? And why was I not informed?"

To this, Moon Jeongyeok replied nonchalantly.

"Well, you did say you had other matters to attend to, Elder. We did not inform you out of concern that it might interfere with your work."

"Does that even make sense? How can you wage a war without me, the strongest force of the detachment?!"

"Hmm, now that you mention it, I might have been too hasty in my judgment. I apologize."

Moon Jeongyeok bowed his head.

"Hmph."

Boyeol snorted, but his anger had clearly subsided.

"Fine, let me hear your plan then. How did you intend to win without me?"

"Please have a seat over here. What are you doing, Fail-Proof Tactics? The Elder has arrived, shouldn't you offer him your seat?"

At that, Jo Gwangwang made a face as if he had chewed on something bitter and abruptly turned to the side.

Then, the Vice Unit Leader next to him turned to the side, followed by a Squad Leader turning to the side, and another one, and another one. Finally, the youngest Squad Leader at the very end got up and stood at the back.

After that, each of them shifted their buttocks to the side, one by one, until a seat at the head of the table was finally empty.

‘They're not going to just get up and offer the seat, huh? They're just shifting their asses, one after another,' Boyeol thought, clicking his tongue disapprovingly as he firmly took the head seat.

But then, the executives of the White Bear Squad under Jo Gwangwang started sliding the teacups in front of them to the side.

Boyeol's lips pouted.

"Am I the only one with a mouth here?"

"It's not tea, but Gyejapju. Are you sure you want some?"

"No, why is it Gyejapju? What's so good about that barbarian liquor?"

Gyejapju was a specialty of Guangxi, a traditional liquor of the Zhuang people, who were considered barbarians in Zhongyuan.

It was made by simmering chicken liver, heart, and intestines, finely chopping them, and then adding them to a cup of liquor.

It was a liquor with chicken innards, a drink and snack in one, a truly barbaric and unfounded culture.

"The liquor is of poor quality, so it needs something like this to be palatable. Or would you prefer Jeoganju instead?"

Jeoganju was a variation where the simmered chicken innards were replaced with raw pig liver.

"Gyejapju sounds better. Give me a cup."

"Do you know how to drink Gyejapju, sir?"

"Do you think I've lived this long without knowing that?"

There are people who just have to make such snarky remarks when they could have just said yes if he knew.

The Zhuang's snack-infused liquor was meant to be downed in one shot.

The liquor was swallowed and the contents were left to be slowly chewed and enjoyed as a snack.

Moon Jeongyeok poured the liquor into a teacup already filled with chicken innards.

It didn't look very appealing, as the liquor was cloudy from the simmered innards.

But surprisingly, it was said to taste quite good.

Especially for drinkers, the taste of chewing on chicken innards with a hint of alcohol was said to be exquisite.

Boyeol took a hearty gulp and crunched on the innards left in his mouth.

The liquor was nothing special, but the innards were savory and delicious.

While he was savoring it, Moon Jeongyeok casually dropped a remark.

"By the way, Elder, I heard an interesting story. That you've been meeting the Heavenly Flower Sword in the dead of night."

"Urk."

Boyeol spewed out the half-chewed innards.

"You know the laws of the Four Evils, don't you? Betrayal is never forgiven."

At that, the executives of the three combat units stood up and drew their weapons.

Their coordination was perfect, as if they had been waiting for this moment.

"Hmph, what do you fools know-"

Boyeol, feeling indignant, snorted. But then, his expression suddenly changed, and he burst out.

"You bastards! You poisoned the liquor!"

"A man who handles the Poison Arts should be more careful. Why would we drink such barbarian liquor for no reason?"

Boyeol's face turned pale.

He thought the cheap liquor with simmered innards tasted bad, but it turned out that the innards were spreading poison, dispersing the Qi in his dantian.

It was Dispersing Qi Poison.

He wondered how much they had put in a single cup, but he drank the entire thing in one go.

"Wait, no. It's not what you think. Betrayal? What glory would an old man like me seek by betraying at this age? Huh? Doesn't that make sense?"

"Then, why did you meet with the Heavenly Flower Sword?"

"Didn't I say I had something interesting going on? The Heavenly Flower Sword was that interesting thing. I planted a viper among those Gyeolim bastards, and that viper is the Heavenly Flower Sword, I tell you."

At that, Moon Jeongyeok burst into laughter.

The laughter spread, and soon everyone was snickering, filling the tea room with their scornful snickers.

"Is that supposed to be an excuse? Why would the Heavenly Flower Sword listen to an old Demonic Adept? What, is she perhaps your hidden daughter or something?"

That was a ridiculous notion.

Especially when coming from someone cornered.

After all, people in desperate situations tended to say nonsensical things.

Look at him now.

Wasn't he just saying whatever came to mind?

"No! That bitch, I was just threatening her with the Heavenly Flower Sword's weakness-"

"Threatening? I heard it was quite an amicable atmosphere. These days, do people threaten someone by reserving the finest guest room and serving them the most precious tea with the utmost care?"

Boyeol's chest tightened.

These bastards were tailing me!

It might have seemed that way to those who didn't know the situation.

In fact, the atmosphere had been quite amicable.

However, Boyeol had not received such treatment for nothing. He had a reason for not ruining the good atmosphere.

"Please listen to me. Rather than a threat, it was more like… a cooperative relationship, I suppose. It wasn't a one-sided, hostile relationship, I'm telling you."

"Cooperation, you say? Cooperation can only exist when there are mutual benefits. What possible benefit could the Heavenly Flower Sword gain from driving out the Orthodox Faction from the Nanning region?"

The Dispersing Qi Poison circulated in his dantian, gradually emptying it.

How much of this damn poison did they put in the cup?!

Cursing himself for not noticing it right away even after drinking it, Boyeol urgently shouted.

"The Blood Cult!"

The Blood Cult.

Just two words, but the weight of the exclamation was far from ordinary.

In an instant, the atmosphere in the tea room sank heavily.

Moon Jeongyeok stopped sneering and asked.

"The Blood Cult, what about them? Why are those worthless pieces of shit suddenly mentioned here?"

The Blood Cult was considered scum even among the Unorthodox Faction.

They were bastards who rampaged, wishing for the end of the world.

The Unorthodox Faction also wanted to live well and eat well, establishing the Law of the Four Evils. They did not wish for the world to end.

"The Heavenly Flower Sword is actually a witch of the Blood Cult! So, for her, if the Orthodox Faction in the Nanning region is destroyed, it's also a welcome event for that bitch."

It was shocking news!

The Heavenly Flower Sword was actually a witch of the Blood Cult!

The declaration, akin to a bombshell, left the tea room in silence for a while, before-

"Pfft."

Jo Gwangwang burst into laughter, unable to contain himself.

Then, everyone roared with laughter, their stomachs almost bursting.

"N-No, Elder, heuk, that's just, keuheuk, you should at least make some sense, kkeuk."

Moon Jeongyeok was practically in tears.

"No! It's true!"

Boyeol shouted, feeling wronged.

Then Jo Gwangwang mocked him.

"The old man has gone senile. What a groundbreaking revelation, shaking the heavens and splitting the earth, isn't it? I'm truly enlightened."

"It's real! She's the White Hand Witch!"

Moon Jeongyeok also joined in the mockery.

"The successor of the Buddha's Palm is the White Hand Witch. Then is she something like the White Hand Buddha? Oh. Doesn't that sound plausible?"

"No! Please! It's! It's real, I'm telling you!"

Boyeol thumped his chest.

He thumped and thumped until his old chest was bruised!

"It's real! It's real, so why don't you believe me! It's real! It's really real! That bitch is the White Hand Witch! She's really the White Hand Witch, I'm telling you!"

"Why, why don't you just say she has mastered all of the Ten Great Demonic Arts Under Heaven? That one hand is white and the other is black, with Purple Lightning Demonic Qi flashing like lightning, while her eyes have wheels turning in them, hm?"

If Qing had been here, she might have suggested that he and the Wudang Sect Leader open a fortune-telling shop together. It was a remarkably accurate guess.

"It's real! And the Black Slaughter Demonic Arts and Purple Lightning Demonic Arts are from the Demonic Cult! They have nothing to do with the Blood Cult!"

"Why, maybe she's a spy of the Blood Cult planted in the Orthodox Faction, but in fact, she might also be a double agent for the Demonic Cult, who knows?"

"It's real! I have proof!"

"Proof, you say. Did the Heavenly Flower Sword confess to it herself or something? What a naive old man."

"The third one there!"

Boyeol shouted desperately.

"He got hit in the cheek with the White Hand Demonic Arts! His cheek must be bruised black with the vicious poison of the White Hand Demonic Arts! Take him to a master of the Medicine Hall! They'll immediately recognize the vicious marks of the White Hand Demonic Arts!"

"It's been a while since the third one got better. What are you talking about, marks? If he was really hit by the White Hand Demonic Arts, his flesh should have rotted and fallen off. Isn't that right?"

At that, Boyeol was stunned.

"Huh? Why? Why is he better? How did he get better?"

It was because the White Hand Demonic Arts used with Daoist True Qi was not that vicious.

"Why are you asking me that? Shouldn't you be the one explaining?"

Boyeol regretted it.

If he had known it would be like this, he should have run away as soon as he realized there was Dispersing Qi Poison.

He stayed, thinking he could persuade them, and now he couldn't even run away.

"The judgment will be made by the Alliance Leader, so for now, you'll have to stay in the prison. I'll light some Dispersing Qi Incense, so if you try anything funny-"

"Isn't it a waste to use Dispersing Qi Incense? Just break his dantian. As long as he's alive, that's enough, isn't it?"

Boyeol's complexion turned pale.

However, Moon Jeongyeok shook his head.

"Don't just read books about sure-to-lose tactics all day and learn some common sense. If you break the dantian of an old man skilled in poison arts, do you think he'll survive? Huh?"

As Moon Jeongyeok tapped his own head with his finger, Jo Gwangwang's face instantly turned red.

Moon Jeongyeok turned back to the Fourth Great Evil with a very satisfied smile.

"Even if a traitor is judged by the Alliance Leader, if he tries to escape, he can be executed on the spot without receiving severe punishment. Do you understand?"

At that, Boyeol slumped to the ground.

"It's, it's real, ha, how, how can this be? Why, aren't there also spies from the Blood Cult in the Orthodox Faction? Even a daughter of the Ten Great Clans was a minion of the Blood Cult, wasn't she?"

"You should say the same thing to the Alliance Leader. He will be the one to judge, after all."

Poison seeped into Boyeol's eyes.

"Fine, I will tell the Alliance Leader everything and reveal how foolishly you have missed this opportunity."

Then, Moon Jeongyeok shrugged and responded.

"Even if what you say is true, how does that change anything?"

"What?"

"According to your words, you have been colluding with an evil member of the Blood Cult. If I were to give you some advice, it would be better to say you were colluding with the Orthodox Faction."

Oh, shit.

Boyeol's complexion turned pale, then gradually became ashen. 