\chapter{Let's Have Some Fun (3)}

The unorthodox martial artists once again swagger through the market.

There were three combat units, and the same number of heads from the Salt Gang's lackeys.

There were many differences between orthodox sects and unorthodox factions, so many that they could not be listed.

However, one of the main differences was that orthodox sects were selective in their recruitment, while unorthodox factions would accept anyone with limbs (and sometimes even those without).

For one, orthodox sects had the issue of martial arts leakage.

Moreover, there were numerous cases of orthodox sects being dismantled after accepting disciples with wicked hearts. So much so that they could have a competition over drinks about which orthodox sect got destroyed by a wayward disciple.

As such, they emphasized a sense of belonging, forming a family-like organization by treating the sect as their family, instilling the spirit of ‘I am the sect, and the sect is me.'

Therefore, they focused on accepting disciples with good character and talent, investing the sect's resources in a small number of individuals to raise them into Masters.

But what about the unorthodox factions?

For unorthodox factions, the lower-ranking warriors were more of a concept of bestowing the faction's name upon them.

As such, for lower-ranking warriors belonging to unorthodox factions, just providing food and lodging was considered a blessing, and even then, most factions charged for room and board.

On the other hand, the martial arts taught were often just slightly modified versions of third-rate martial arts that could be found in the market. One could say they were, at best, second-rate and a half.

If one wanted to learn good martial arts, they had to prove their worth through achievements and catch the eyes of the executives.

Or they could do so by currying favor through flattery and offerings.

So, one might think it's a battle between a small elite force and a large tactical force, but in reality, it wasn't as if unorthodox factions were lacking in Masters.

It's just that the orthodox sects were a bit more robust in the middle ranks, while unorthodox factions had dozens of legs attached?

Then one might ask if the orthodox sects were weaker, but the fact that most sects that have lasted throughout the long traditions were generally orthodox showed the importance of the righteous path.

After all, whenever unorthodox factions grew large, they inevitably split due to internal strife or the leader was replaced, never lasting long.

Therefore, if the orthodox and unorthodox factions clashed (over the control of the local area), the battle itself would be a defeat for the orthodox.

However, if losses occurred during that process, the balance between factions within the unorthodox would be broken, executives would be replaced, and even the position of the leader would become unstable.

So, most of the time, the unorthodox factions would not initiate fights.

What's the point of taking over a territory if it might end up being handed over to someone else? It's better to maintain the status quo and lord over it.

But the unorthodox faction had aggressively supported and dispatched three combat units.

Moreover, two White-Rank and one Black-Rank combat units were a force that could overwhelm even the Gyerim Sword School, were they not?

On top of that, there were plenty of third-rate lackeys from the Salt Gang who would have at least done their part if they could just scratch the enemy before dying.

For these reasons, a heavy and solemn tension hung among the orthodox martial artists gathered at the Changshan Martial School in Nanning.

Even though there were more Masters on their side, one could not help but wonder how many would survive.

This was the strength of the orthodox sects.

Even in the face of clear disadvantage, they stood their ground, albeit with somber expressions. After all, where else could they go, abandoning their homes and families?

If it were an unorthodox faction, one would have witnessed a miracle of people rapidly disappearing in real-time.

After all, shouting ‘Abandon ship!' on a sinking vessel was the spirit of the unorthodox.

Thus, with the wide-open gates of the Changshan Martial School in front of them, Sect Leader Kang Suyang and Union Leader Yo Hwancheol looked at each other from a distance.

For some reason, in Zhongyuan, there was always a sequence where someone had to step forward and talk before a battle.

This was a tradition that had come down from ancient times, even more primitive and barbaric than now.

It was a time for psychological warfare through words and actions.

It was no different from how the swarthy individuals of the far west would insult each other with rhythm and rhyme. It was a truly astonishing occurrence.

It was because all of humanity shared the same roots.

This was due to the influence of the Great Huan Empire, a nation of the great and noble Korean people that existed even before the birth of the universe and was the progenitor of all mankind.

The evidence of this truth could be seen in the Subakdo1.

-is what some idiots in Qing's homeland still claimed to this day.

At any rate, the famous line, ‘I pity you for having three fathers', was also a moving speech that came from such psychological warfare just before a battle.

Victory through initiative!

Just as Yo Hwancheol was about to open his mouth…

"The salt peddler has come. However, the warehouse is already full of salt, so there is no need. You may leave."

Kang Suyang struck first.

The effect was remarkable!

"Who are you calling a lowly salt peddler?!"

"Then, you are not a salt peddler? Then what are you?"

"I am the leader of the great Yoga Salt Gang, Yo Hwancheol!"

"Isn't a salt gang a place that makes salt? If the leader of a salt gang is not a salt peddler, then what is he? I am genuinely curious and asking."

"I am……!"

Yo Hwancheol could not continue.

Because he was, in fact, a salt peddler.

"And I did not even say you were lowly. Where is there any high or low in this world? How can one differentiate between the head of an orthodox martial school with three hundred years of history and a mere salt peddler? I do not think that way. At least, I do not."

That's just what I think, though.

Everyone in the world knows you're lowly, you see?

Wow, that uncle is really good with his words.

Qing's ears perked up.

Wow! How can he insult so elegantly like that?

If it were me, I would have said something like, ‘Oh, is being lowly bothering you?

‘Did you get it from your father or your mother? Or both? Ah, but I guess it's still certain that your children will be lowly for generations because of their father.'

It would have been a rough and vulgar insult that only ruffians in the marketplace would use.

Truthfully, in terms of taking the initiative, Qing's words and actions were a thousand times more painful.

However, such crude language would also harm the speaker's dignity.

It seems one can't just become a Sect Leader for nothing.

I could never insult like that.

Thus, Qing listened attentively, adopting a learning attitude.

All while hiding in a teahouse across from the main gate of the Changshan Martial School, behind the unorthodox martial artists.

Qing was assigned to the rear ambush team.

Ambushes were laid behind the walls, waiting to strike those who crossed over, while those who entered through the main gate would be surrounded and cut down.

And as Qing had strongly asserted that she could take care of herself, she would immediately strike the rear as soon as the battle began.

The Wulin Alliance's guests could not be assigned such a dangerous task.

However, what if it was not dangerous?

"I don't understand why we have to make each other feel bad when we're going to fight anyway."

"Well, if you can raise morale by just wagging your tongue a bit, how great of a benefit is that?"

"But isn't he losing?"

"Well, since his eloquence hasn't been widely acclaimed, that salt peddler must have prepared some words of his own. Like, surrender or I'll let the rest go if you crawl between my legs."

"How childish. What is it with men?"

The woman shaking her head was Lady Chang, Transcendent Realm.

"Hehe. Then, this is all just to play a game of land ownership. How childish. Oh my, Young Lady, I did not mean that remark for you. This old and thoughtless man has made a slip of the tongue."

The suddenly humble old man was Old Man Gyun, Unrestrained Realm.

The one who kept picking up things and handing them over was a hopper, also at the Transcendent Realm. Meanwhile, the man dressed as a scholar, who kept handing over brushes or paper, was called the Illiterate Poet, and he was also at the Transcendent Realm.

They were the guests sent by the Royal Palace to assist Qing.

Along with Qing, there were four at the Transcendent Realm and one at the Unrestrained Realm, plus one Peak Realm leech, making up a formidable force of six.

At this point, it should be called the main force rather than a detached force.

"It seems the Salt Gang Leader has stepped down and another has come forward. It looks like it will be a while, hehe, Young Lady, but are you not curious about what a jade tongue is? Here, I have some preserved plums."

"Wow, what is this? Thank you, I'll eat it well."

"Oh, no, it is nothing. I just picked it up along the way. Hehe."

At that, Qing, who was reaching out with her long and slender fingers towards the jar, paused.

What? Did he mean he picked it up from the ground?

"Ah, it was just lying there, jar and all."

"Where in the world do you keep picking these things up?"

"Hehehe, that hopper bastard is bribing her again……"

Lady Chang muttered.

Of course, even if he had actually scraped it off the ground and put it in a jar, she wouldn't have refused it.

As Qing was giggling and about to reach out her hand, another hand reached in first and picked up a round plum.

It was Nayang Gyeol, who had stuck with Qing until the very end.

"Here, my little bear. Ah, if you will?"

"Can't you see I have my own hands?"

"But I do not want my little bear's beautiful fingers to get dirty? Your fingers are national treasures. They must be protected. Ah."

"Ah."

"That's right. You eat so well. Kya."

Nayang Gyeol made a fuss and quickly pulled his hand back.

It was because she had put her fingers in her mouth as if to feed her, so he had no choice but to respond with her teeth.

"This one is acting up again."

"Look at this. My little bear's teeth marks. Were you trying to leave your mark on me?"

"Try doing that one more time. You said you're an expert in Kicking Techniques, right? It doesn't matter if you lose a finger or two, right?"

"Wouldn't that be fine? Every time I see a severed finger, I will think of my little bear and my heart will flutter."

Qing munched on the sweet preserved plum and waited for the war of nerves to end.

Then, soon enough…

"Further conversation is useless! Charge!"

At that, the Salt Gang warriors shouted and charged forward as the vanguard.

They were, at best, third-rate.

They couldn't even properly climb over a wall that wasn't even one zhang2 high, struggling and clinging to it. Meanwhile, those who were pushed into the main gate just tripped and fell.

"Ambushes! They're ambushes!"

What ambushes? They're just throwing rocks.

However, for those at the third-rate level, a rock thrown by a Master was no different from an ambush.

"I can't watch this, Second Unit!"

At that, the Black Bear Unit warriors roared and charged.

They ran with high spirits, but they pushed the Salt Gang warriors clinging to the wall over, using their strength to help them cross.

Thus, the Salt Gang warriors, barely managing to cross the wall with the help of their Senior Brothers, screamed in gratitude, "Euaaaah!"

Since placing obstacles under the walls was a basic common sense of defense, the screams were all too understandable.

Only then did the Black Bear Unit warriors leap over the wall, landing on the bodies of the Salt Gang warriors who had fallen into the traps, and raised their weapons.

From ancient times, the best way to overcome obstacles was to push people through.

"Third Unit!"

At Jo Gwangwang's shout, Qing also jumped up from her seat.

"Well then, let's go!"

Qing kicked off the eaves of the teahouse, causing dust to rise and leaving a deep footprint on the floor.

Perhaps due to the aftereffects of vomiting blood earlier, her bloodstream circulated rapidly, warming her entire body.

Qing shouted with a wide smile!

"The Moonlight Sword is famished! So weep, for I shall offer you the Infernal Demonic Ocean Blade!"

The Moonlight Sword's (No. 10) heavy blade was thickly coated with sunset-colored Sword Force.

As she turned her head to the voice of a woman, a Salt Gang warrior's neck, who had been looking back, was penetrated by the Sword Force.

According to the law of inertia, the Salt Gang warrior's neck, which had turned an extra half-circle, was cleanly lopped off and fell to the floor.

Yes, this is it! This is why I live!

A beat later, the guests of the Royal Palace joined in.

And there was one pretty leech from the Heavenly Flower Hall who had promised to protect Qing.

There were two White-Rank combat units, mostly composed of First-Rate martial artists.

However, in Qing's detached force, the lowest-ranked was Nayang Gyeol, who was at the Peak Realm.

Moreover, the nets and iron weights used to subdue Masters had already been given to the first wave.

In an instant, a scene of crimson carnage unfolded.