\chapter{Fire In Chang'an (8)}

"Do you think Jangheung Corporation is some kind of a corner store? Would they start a business just to make a few gold pieces? So what can you do? Cut down on materials, use cheap substitutes, and fill it with stones."

Qing's eyes narrowed.

This guy was just spouting nonsense with that loose mouth of his.

"Over two thousand people died in Nakseong. Some say it's over three thousand if you include the missing. What do you mean missing? They just couldn't find the bodies."

The carpenter Jang's expression darkened.

"It was just bad luck. I made sure to do the construction properly, at least for the key pillars. If it hadn't rained so damn hard."

"It's not because of the rain. It's because of you."

"If the design had been a little cheaper-"

"Don't blame the design. From what I hear, it would have collapsed anyway, even if it wasn't an expensive design. Since you were going to build it shoddily to pocket the money, how could it withstand such rain?"

"Ummm……"

"Tell me. If the cost of construction was cut in half, do you think you would have built it according to the design?"

"Um……"

Jang just made uncomfortable groans.

It was the reaction of someone who had nothing to say.

The excuse that it was too expensive to follow the design, so they had to cut corners and use cheaper materials, was pure bullshit.

Would those who pocketed money care about such things?

If the design had been cheaper, they would have pocketed even more and done the same thing, so it would have collapsed anyway once the heavy rain came.

"What awaiting the afterlife, my ass. What afterlife is there after taking the lives of three thousand people? In my opinion, you'll be stuck in hell and get hacked to pieces until the world ends."

"Damn it……"

"So, who ordered it? I heard that a lady at Jangheung Corporation was in charge of the construction. Did that bitch tell you to cut materials?"

"Yes. It was her. Everyone was worried. But what can you do when the boss tells you to? If you defy Jangheung Corporation in the Shaanxi construction scene, you might as well consider your career over."

It was an excuse that he had only followed orders.

However, Qing could see Jang's Evil Karma.

It was too high for someone who just followed orders.

Besides, Qing was a baby carpenter.

She had heard stories from carpenters.

"I've done some carpentry work myself, you know? Did you personally pocket some materials too, mister?"

"Every carpenter in the world does that……"

"I bet. The corporation pockets some, and the master carpenters each take their share, so what did you even build it with? Was it just mud, like some kid playing with clay?"

"……"

"So that's why you die secretly in a shabby room like this. You're not in a position to blame or resent anyone since it's a natural death. What's so unfair and sad about a piece of shit dying?"

"Ugh. I'm a dead man, but before I die, I have one last request. I have some hidden gold and silver, and I want to leave it to that bitch of a wife and my children… Keok."

Jang, who was about to say something, suddenly made a choking sound.

It was because when a foot stomps on your neck, no one in the world can continue to speak.

Qing replied with an expression of disbelief.

"What is with this guy? Do you think I'm here to listen to your will because I have nothing better to do? And why would you pass on money earned from people's lives?"

Since the right side of her stomach had a huge chunk of ice sticking out, the carpenter Jang struggled and thrashed with his remaining left arm.

Carpenters were people who were trained with practically compressed muscles, but at best, they were only slightly better than ordinary people, barely able to brawl with gangsters.

Qing was a Master who had reached the Transcendent Realm.

The carpenter's struggles gradually became desperate, searching for air more intensely.

But Qing's foot was like a mountain, firmly blocking his breath.

Thus, with a snap, like a thin thread breaking…

The desperate struggle, which had been using all its might, crumbled in an instant, at that very peculiar moment.

"Phew. What a waste of time. Hey, are there any other guys?"

"If an assassin has been deployed, it would be too late to find more. Besides, this kind of tracking is what assassins are specialized in. After all, these kinds of hideouts are not places that inspire trust in that regard."

These hideouts inevitably touched upon the Lower Gates or similar groups of the underworld.

And since assassins maintained a close relationship with them, it was a poor choice to hide from assassins in such places, even if it was good for hiding from others.

"Hmm. Well, I guess that's that."

Qing scratched the back of her head.

"I was told to spread the word around town and ruin them. There aren't any witnesses. I guess I'll just have to catch that Jangheung Corporation lady, make her confess that there are more to kill, and then, hmm… I'll cut off her limbs and deliver her to the families of the victims in Nakseong."

After all, the best cure was revenge.

Strictly speaking, it was more of a closure than a cure.

The pain of losing a family member only fades, so revenge can never truly heal.

But it was certainly the best way to help tie up the knots of hatred and resentment, helping one move forward.

"If you want to publicize the misdeeds of Jangheung Corporation, there are still plenty of witnesses left."

"You said the rest will die anyway, didn't you? And there's no way to find them faster than the assassins."

At that, Seol, that guy, offered a solution.

"So if we catch the assassin, wouldn't it be solved? If the assassin testifies that they received an assassination request, people aren't stupid. Obviously, they will think there's something fishy when all the city carpenters are dying."

"Wow! As expected! From now on, I'll acknowledge you as the region's greatest intellect. The neighborhood is too small to contain this brilliant mind. Go out into the bigger world. Yes. Yes. Indeed, the greatest intellect in Shaanxi!"

Qing upgraded Seol, that guy's, evaluation.

Seol, that guy's expression was uncomfortable.

"There are many truly intelligent people, so what am I. It's embarrassing, so please stop saying that."

"Such humility too."

"Seriously, stop it with that……."

"Anyway, how do we find an assassin?"

"What's so difficult about finding an assassin? They're people who kill for money. If we just investigate those who receive money, we'll find out. I'll look into it, so let's go back for today."

"Reliable! Trustworthy!"

"Anyway. People really are."

Even so, the way his lips slightly curled upwards showed that he wasn't feeling too bad.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In Zhongyuan, there was no saying like 'trying to catch a louse and burning down the entire house'.

This was because it was a Korean proverb.

There were various theories about the origin of this proverb.

One theory was that a macho man, annoyed by the constantly appearing lice, just burned down the whole house.

It was said that being bitten by lice was incomparably more itchy than a mosquito bite, so those who had realized the itch and couldn't sleep at night could roughly understand the frustration.

Or, it was said to have originated from the traditional insecticidal method of catching lice.

To catch lice, they burned insecticidal herbs like mugwort or duckweed to fill the house with smoke. Then, sparks would fly and a house made of straw would quickly burn down.

In Chang'an, a fire was spreading like this.

Of course, Jangheung Corporation was too big to be treated as a louse, and a large city like Xi'an wouldn't burn down from just a few sparks.

But sparks that started from the flood in Nakseong had reached Chang'an, and at first, Jangheung Corporation, feeling guilty, tried to eliminate the technicians.

However, the embers were not properly extinguished, and this time, the flames spread to the assassins.

Thus…

Targeted violence covers the assassins!

Though, since they were bastards who killed people for money, it would be fine even if it was violence without a cause.

So, it was too much to call them assassins.

Since there were righteous assassins in the history of Zhongyuan, these people were called killers, to elevate them.

The landscape of the assassin industry in Zhongyuan was such that five major organizations, namely the Killing Star, Killing Net, Killing Valley, Jelim, and the Heavenly Slaughter Gate, each occupied a region.

The most skilled and expensive assassination group among them was the Killing Star.

But recently, the Killing Star had closed its business.

However, not many people found it strange, because assassin businesses were always at such risk of going under.

Thus, the hot topic in the assassin industry, the talk of Chang'an, was how and why the Killing Star guys had been wiped out overnight.

And another really big question.

The assassins of the Killing Star wouldn't have all died without exception, so why were there no survivors among those famous for their skills?

If they had just appeared, people would have offered vast amounts of gold and silver to recruit them, licking their lips in anticipation.

What the world didn't know was that the infamous assassins of the Killing Star had, in fact, merely changed their jobs.

Now, there are no assassins in the darkness.

They were just basking in the sunlight under the new Heavenly Demon, enjoying the warmth, having love affairs, making friends, sharing the warmth of neighbors, and sometimes even starting families, thinking this was truly the joy of living.

And since all this grace was bestowed by the great Heavenly Demon, wasn't it a faith that should be defended with one's life!

The agents of the Secret Unit (formerly assassins) were all about the Heavenly Demon Supreme.

It was because they were humans whose heads had been thoroughly messed up by the extreme brainwashing techniques the Heavenly Demon Divine Cult had systematized and perfected over a long period.

It couldn't be helped since if they weren't brainwashed like that, the Secret Unit agents dispatched to Zhongyuan would immediately apostatize and defect.

The assassins knew best how the assassin industry worked.

Therefore, the Sun-Moon Escort Agency already knew the locations of all assassin agencies in Xi'an.

Thanks to this, Qing was able to obtain a booklet containing the locations of all assassin agencies in Xi'an as soon as she finished lunch the next day.

"Wow, so quickly?"

"It turns out the escort agency had the information on hand."

"Ehh? Why would an escort agency have information on assassins?"

"How should I know? But isn't it common for large businesses in the city to make connections and increase their clientele, asking to use their services?"

"Phew, phew, haaaaa……"

"I guess it's not like they suddenly raided an agency and found a ledger of Sun-Moon Escort Agency, right?"

"If that were the case, they wouldn't have handed over the information so readily, would they? It shows they have confidence that they have no connection with them."

"Hot, haaa, ha, hot, ha……"

Hmm. Why is he eating his food so messily?

Qing looked at Seol, that guy, who was somehow managing to cool down the boiling soup by blowing on it, taking deep breaths in and out.

It wasn't just soup, but a snake soup called Five Snake Soup.

As the name suggested, it was a health food made by boiling five types of snakes, and it was a very, very expensive dish.

However, this Five Snake Soup was a Guangdong dish, and in Guangdong cuisine, soup was more like a thick, viscous liquid with starch, with the temperature of boiling oil, so it could be called a lava soup.

No, wait, how can he eat that without even cooling it down?

Is he human? Isn't that some kind of a magic show?

Of course, it had been boiled before serving, so it wasn't actually boiling oil, but still, the thick soup, half of which was oil, would be much hotter than boiling water.

Hmm. Well, it's not like I should criticize someone else's eating habits.

It's not like it's harming anyone, and it's interesting to watch, so whatever.

"So, we can start cleaning them out from tonight. Hmm. Where should we start?"

What a delight it was to have a whole bunch of bastards who killed people for money.

This was practically an all-you-can-eat buffet, a free pass!

Qing couldn't suppress the humming that naturally came out.

Although they were famous folk songs of the Korean people that did not yet exist, it wouldn't matter since the concept of copyright did not exist in ancient China.

It was just that those who heard it found it very pleasant to listen to. 