\chapter{Fire In Chang'an (10)}

Even in the world of assassins, there are different ranks.

Surprisingly, assassination requests were not common in Zhongyuan.

This was because if there was someone you truly wanted to kill, you could simply kill them and run away.

The Zhongyuan was vast, and if you ran far enough, no one could find you.

If the victim was an ordinary commoner, the authorities wouldn't even bother to pretend to look for the culprit, so there was no need to run far.

Thus, the Chinese people had a savage streak in their blood, thinking, 'Let's not just kill, but kill and disappear' rather than just 'I want to kill'.

However, if you didn't want to run but still needed the bastard dead, then you could hire someone else to do it.

These clients belonged to the same rank.

For these requests, they didn't use professional assassins.

If the target was an ordinary commoner, there was no need to mobilize an assassin, as there were always desperate people who would do it for free.

Mainly those who had lost everything at the gambling dens.

Some were victims of scams, or others were debtors with unfortunate stories.

If not for Qing, there would have been a surge of such cases in Nakneung.

And if the target seemed wealthy or the request was clearly not about killing ordinary commoners, then they were treated as Silver Rank.

The room Qing entered was of the Silver Rank.

Then there was the Gold Rank. From here on, it involved professional killers, those who made killing their profession, taking on these requests.

These were also expensive requests that were handled by assassin groups that dominated the area.

Above that was the Special Grade, but they didn't have a separate counter for receiving clients.

This was because Special Grade clients were the decision-makers of large merchant guilds, high-ranking officials, or top figures like the leaders of the largest martial clans in the region.

Since they had established connections and made their introductions, there was no need for a counter where clients would come to them.

Qing thought that this information was worth more than a single tael of silver.

If Jegal had been around, he would have rattled off this kind of information just to pass the time.

Hmm. What a pity.

But since you couldn't pay the price, you can't save yourself either.

Also, now that I've heard about it, it seems quite systematic. If killers have such a system, how long have they been in this business?

What a disgrace. Death penalty.

As a result, the two thugs who were kneeling and trembling pissed themselves.

"Ugh. How dirty. Why are grown-ass men urinating indoors when we're not even outside?"

"P-Please, spare us. Please. We'll be good. We'll live kind lives."

"Hmm. Alright. Live kind lives. I'll let you go just this once since you said you'll live kind lives. But there won't be a second time. Do you understand?"

"Yes! Yes! We'll live kind lives!"

However, the two should have been feeling wronged rather than grateful.

Both were just barely short of a hundred points of Evil Karma.

They looked intimidating, but they were the type to just stand around as folding screens. It seemed like they hadn't done anything too outrageous yet, surprisingly.

"I'm sparing you because you don't seem like really bad guys."

"Yes, yes!"

"Th-Thank you!"

Although their pronunciation was unclear due to their trembling, the two immediately switched from kneeling to prostrating upon hearing they would be spared.

When the door was knocked, the thugs guarding outside unlatched it and opened the iron door with a creak.

Only after the smell of blood and urine wafted out did the thugs' expressions change.

A hundred and twenty-one, a hundred and seven.

Close, but a pass.

They hadn't brought their weapons, but Qing's body was practically a transcendent human weapon.

One's left hand was the White Hand, and the other was the Black Hand.

It was an astonishing sight to see the two Hand Techniques of the Ten Great Demonic Arts Under Heaven being used by one person.

Hmm. The Black Slaughter Demon's Palm feels a bit better in my hand, though.

But did it come from the left or the right?

While Qing was looking from side to side, wondering which one it was, Seol Ri gently tugged at Qing's sleeve.

It was a subtly helpful gesture.

As Qing advanced, the corpses lined up along the underground corridor. They were either the guards who had been guarding the doors or those who had been on patrol.

Of course, there were a few living ones among them.

"Ah. Shush, no, no, no, tsk. Guk-nyeong-ah, no. Not him. Let him go. We'll spare him."

Seol Ri, who had been grabbing the necks of low-level thugs and smashing their faces as if she was having a great time, looked up at Qing as if asking why.

But why is she using her fists instead of her Ice Arts?

"Shush. He's okay. Bite that one instead. No, hit him."

"Yes."

Despite not knowing why, she listened well, which was quite lovely.

Sometimes she'd be stubborn, but Seol Ri was generally obedient.

"I don't like being called Guk-nyeong."

-she thought, right as she was about to rebel.

But still, it felt like the child was becoming more docile, perhaps because in the past, she would have just said, 'Don't call me Guk-nyeong.'

There was a huge difference between 'don't call me that' and 'I don't like being called that'.

"You're using an alias, so bear with it for now."

"You said Gun-yeong, not Guk-nyeong."

"It's hard to pronounce. Gu nyeong. How's that?"

"You said Guk-nyeong again."

Qing's mischievousness was suddenly piqued.

Originally, Qing's way of showing affection to animals was quite mischievous.

But honestly, wasn't it a perfect fit?

In a group, the one who's always lacking is called a hole.

And Guk-nyeong-ie really lacked in many areas, almost the very definition of lacking.

So, among all holes, she was the biggest hole.

A true beauty who would be embarrassed to be put on display anywhere.

If only her face wasn't to my taste…….

"I thought it was a term of endearment. Guk-nyeong-ie, um. Isn't it cute and nice? Can't you just be called Guk-nyeong-ie?"

Seol Ri thought for a moment and then answered.

"I still don't like it."

"Why? Guk-nyeong-ie. It's cute, isn't it?"

"It's not cute at all."

"It's cute to me. Can't you do it?"

"……I still don't like it."

It seemed like she was hesitating a bit, so maybe if I pushed a little more, but…

It seemed like she really didn't like it, so I guess I should stop here.

And so, Qing cleared the path of blood.

Of course, when talking about clearing a path of blood, it usually meant paving a way with the blood and sacrifices of oneself or one's allies, but since the corridor was soaked in a straight line with the blood of her enemies, it could still be called a path of blood.

Then, turning a corner, a dazzling golden door came into view.

It reminded her of the words of the deceased receptionist or broker, who had said that it was obvious at a glance.

Wow. It really is obvious at a glance.

The doorkeepers, seeing the blood-covered pair, immediately shouted.

"Who are you bitches!"

"It's me!"

"Intrud-"

At the same time, the guy tried to reach for his neck, pulling out a string and quickly grabbing something attached to the end. However, Qing stepped hard on the ground and shot forward like a bullet.

Qing's hand, with a whitish Sword Force, pierced through space, leaving a straight afterimage. The guy looked down at his chest in disbelief.

To be precise, he was looking at Qing's right hand, which had pierced his solar plexus and only showed her white forearm.

Regardless, Qing yanked the whistle hanging from the man's neck.

It was black and small, just about two finger joints in size.

"Yeah. This. It looked like this. I remember it right away when I see it. Wow. Memories are flooding back. But they're not good memories, are they?"

Qing had a deep aversion to the sound of that whistle.

It was a dirty memory of being herded like animals with those whistles blowing all around.

But now there's a whistle that was used to make that sound, right here?

"Keoheuk."

Meanwhile, as another guy was stealthily feeling for his necklace, Qing hurriedly threw the whistle she held.

"Ack!"

She would have aimed for the eyes if she wasn't in a hurry, but she ended up hitting him right in the forehead.

Considering it was a small whistle just two finger joints in size, the sound of impact against the forehead was quite loud.

The power was also considerable, as the man's head jerked back violently.

And at that moment-

A sound of something pouring down got closer, and a white chill brushed past Qing's cheek.

White frost, burning like a flame, took the shape of a dragon, its frozen scales rattling as it wrapped around Seol Ri's arm, rising from her shoulder.

Then, with a refreshing burst, Seol Ri's palm struck the enemy's chest, and simultaneously, the frost dragon at her fingertips burrowed into the enemy's body.

Wow. What's this! How cool is that!

Qing had forgotten to pull out the hand she had thrust into the gatekeeper's chest and couldn't help but exclaim in awe.

The sight of a beauty flying with a frost dragon was truly a picturesque scene, a spectacle of coolness.

If it were winter or raining, she could have seen an Ice Dragon, but Seol Ri's performance that Qing had seen at the mountain cottage was nothing more than fleeing, getting beaten like a dog, and being dragged around by her hair.

While she acknowledged that Seol Ri's poisonous scheme to take revenge by feeding the enemy frozen limbs was quite impressive, apart from that, her actions were hardly those of a martial artist.

But our Seol Ri-ga!

"Keugh."

The guy who was directly hit in the solar plexus by the Ice White Divine Palm stumbled back, his breath caught more by the physical shock than the cold.

At that moment, another frost dragon emerged from Seol Ri's opposite shoulder, and her outstretched left hand struck the solar plexus again.

Crunch. It was an audible sound.

The guy, with his chest caved in, vomited blood and collapsed.

Hmm. But isn't it supposed to be Ice Arts?

Then shouldn't it freeze things or something?

Why are his ribs shattered?

"Kkeugh……"

Qing's thoughts were interrupted by a gurgling sound.

Oh, right. My bad.

Only then did Qing yank out her hand, which had been warmly heating up inside someone else's body.

The gatekeeper, who had been desperately holding onto Qing's wrist, couldn't overcome the strength of a monstrous woman who had reached the pinnacle of human strength.

"Wow. Our Ri. Just now, you seemed like a real martial artist. You looked cool. I'm starting to see you in a new light. Seriously."

"……?"

Seol Ri tilted her head-

"A real martial artist? Then until now-"

"Alright, alright, never mind that. Was that the Ice White Divine Palm? That was so cool. Why did dragons appear? Shouldn't Buddhas appear if I use the Buddha's Palm? Honestly, I'm a bit jealous. It can't be that just because it's purple, no, I mean, it's called a Divine Art for a reason."

Seol Ri's lips curved ever so slightly.

If it were Qing, who specialized in raising Seol Ri, she would have interpreted that expression as one of being quite smug.

Qing wasn't just paying lip service.

After seeing it with her own eyes, she really did become envious.

What's this? Why is it so cool?

But I guess it's understandable, since its effect wasn't really shown. Maybe it's because her Inner Qi level is only at the level of a mere First-Rate or something.

"Can you show me one more time?"

"Yes."

At that, Seol Ri summoned several small frost dragons with a whoosh. It seemed she could summon several small dragons, as cute baby dragons wrapped around each of her arms, circling up to her fingers before dissipating.

"Originally, it should be an Ice Dragon. But it's too hot."

Seol Ri said that it wasn't because her Inner Qi was lacking.

Seeing Qing's envious gaze, Seol Ri tried to say something-

"Hmm. Show me again later when we get back. Let's finish what we were doing first."

Qing pushed open the golden door with force.

Inside, a Gold Rank receptionist, who had been lounging with his legs up on the desk and his arms behind his head, was startled.

So startled that he actually fell out of his chair in his haste.

It seemed the soundproofing of the room was indeed effective, as he had been dozing off, unaware of the commotion outside where his colleagues had fallen.

At the same time, two men standing behind the fallen receptionist, with their hands behind their backs and faces covered, rushed towards Qing.

But the speed at which they moved was such that by the time the receptionist hit the ground, they had already reached Qing, their presence suddenly filling her vision as if they had sprung from the earth. 