\chapter{Fire In Chang'an (9)}

Qing had no idea there were so many assassin agencies in the city.

Of course, it wasn't surprising that she didn't know, since Qing generally
knew nothing at all.

However, this time, it was something that no one, unless they were in
the business, would know, because this market had suddenly grown and
the number of agencies had increased.

Originally, there were only two or three agencies in the city, and they
were usually set up in the black market.

But since the black market had suddenly gone into hiding, the assassin
industry, which was struggling to meet their clients, had opened several
civilian agencies in the city to take on requests.

As such, the system was not yet properly established, so although Qing
didn't intend it, it was the perfect time to stab the assassins.

However, the fact that the black market went into hiding was entirely
due to Qing, so she had, in fact, created this favorable situation herself.

It was no coincidence that the heavens helped those who helped
themselves.

It was a seedy teahouse in a not-so-great part of the commercial
district. If one went past the smelly area towards the backyard's
outhouse, a shabby, semi-basement door would appear.

Upon opening the door and going down to the basement, a surprisingly
well-maintained facility appeared. Muscular, tough-looking men with
dirty faces and swords strapped to their waists were standing guard
everywhere.

Hm. Small fries.

Qing thought to herself.

In Zhongyuan, muscular men with dirty faces were considered
the weakest among martial artists.

It was usually because they were third-rate thugs who only knew how to
swing a sword without any formal education or proper martial arts
training.

Therefore, they might be great for intimidating ordinary citizens who
came to make requests, but to the eyes of Qing, a Transcendent Realm
Master, they were just a bunch of incompetent, insignificant lowlifes.

To put it bluntly, they were as pathetic as Seol Yiri……

"Sigh."

Qing sighed deeply.

She wasn't really in a position to criticize the assassins for
swaggering around with such pathetic underlings.

After all, beside Qing was none other than the epitome of incompetence
herself, the young lady of the Seol Clan.

Seol had some work to do today for the Seol Family Trading Company.

Of course, they didn't come alone. Gramps was waiting outside.

He said he had set up a perimeter with the trading company's
guardsmen in case Qing missed anything.

The trading company's guardsmen, really? How pretentious.

Honestly, Gramps could just say they're Demonic Cult bastards from
the north. It's not like anyone would particularly care.

While Qing was having such thoughts, she was walking down into the
basement.

Then, as she reached a door painted silver, the two Seol Yiris, no, the
two incompetent underlings guarding the door, lowered their voices.

"Take off your veil and write your name."

"Hm. You'll give it back later, right?"

"Quickly."

This was something Seol had told her about in advance.

What better way for assassins to ensure their safety than by holding
their clients' identities hostage, threatening them not to betray them
otherwise their lives would be at risk?

Of course, they wouldn't dare ask for the identities of truly influential
people, as those in the back alleys were inherently weak against the
strong and strong against the weak.

Thus, Qing and Seol Yiri took off their veils, momentarily illuminating
the dim basement.

Two of the Six Flowers of Wulin were radiating their brilliance.

"……"

As if entranced, no, they had actually been entranced, the two Seol
Yiris, no, the two incompetent scraps, just stood there with their
mouths agape, staring blankly.

"Hey, aren't you going to give me the registry?"

"Ye-Yes, here it is, I mean, here."

Qing then obediently wrote their names in the registry.

It was a handwriting that would make a court academic marvel and the
Greatest Under Heaven admire.

A-Qing. Seol Gunyeong.

She didn't even bother coming up with a fake name.

Third-rate thugs had no ability to discern handwriting because they were
illiterate. To them, white was paper, black was letters.

Upon entering, they saw a guy wearing a bamboo hat, sitting at a table
with a certain air about him.

There were two men standing on either side and behind him, putting on
airs.

"Whew. How did such beauties come to such a rough place? The one
who is to die must have committed a grave sin, indeed. So, which
bastard shall I kill for you?"

The guy in the bamboo hat whistled once and spoke in a low voice.

Men thought that lowering their voices made them sound cool, and the
guy in the bamboo hat was also a man.

"Do you know a carpenter named Jang Yeok? He's a famous master
carpenter."

"Master Carpenter Jang Yeok. Very well. Normally, this request would
require a Gold Unit, but since I feasted my eyes on such beauty today,
I'll do it for just six Silver Units, exactly half price."

Qing frowned at this.

"How can you kill someone who's already dead? Why, are you trying to
take six Silver Units for free, saying you'll kill a dead man?"

"Ahem. It's usually in this line of work that you get scammed if you
don't know any better. So if it's not killing someone who's already
dead, what is your request?"

"I want to know who killed Master Carpenter Jang. How much to bring
that person to me alive?"

"Well, well."

The bamboo hat spoke in an irritatingly languid manner.

"Look here, young lady. Even if we're a bunch of lowlife human trash,
we still value loyalty. How could we sell out our own for money?"

"Ah. So you're all one big happy family?"

"If you offer, say, twenty Gold Ingots, the higher-ups might consider
it."

"Twenty ingots? You're no different from a robber."

"Do you have any more questions? Well then. The consultation fee is
three Silver Units."

Then he slid the silver tray in front of him forward.

Qing asked again.

"Gold is out of the question, but what about paying with my body?"

At that, the bamboo hat paused.

"With your body, you say? Hoho. Well, with a beauty like that, young
lady……"

Then a finger poked Qing's side.

When Qing turned her head, Seol Yiri, with a serious look and furrowed
brows, was looking at her.

"You can't do that."

"Why? Do you have another way?"

Seol Yiri's eyes shook uneasily.

Then, suddenly, she firmly grasped Qing's hand and spoke in a
determined voice.

"Then, I'll do it instead."

"Huh? Why would a hole like you do that?"

"I'll protect you."

"Hehehe, this is truly a beautiful friendship. Then, why don't you both
pay together? Are you perhaps a virgin? In that case, I can give you a
higher pric- Ah, eup."

The bamboo hat, who was babbling nonsense, suddenly had his jaw
grabbed by the most beautiful and evil hand in the world, the Small
Demonic Hand.

"You know, what you see is what you get. Your head is full of such
vulgar thoughts that when I say paying with my body, you think of that
shit, huh?"

"Eup. Eup."

The bamboo hat's eyes trembled.

And so did Seol Yiri's, who was looking at Qing.

"Ah, I'm not insulting holes. Um. I'm impressed, honestly? Your
willingness to sacrifice yourself is really commendable."

As Qing said this, she felt the bamboo hat's hand that was clinging to her
arm.

And then, she lightly snapped off his little finger.

It was a very light gesture, like plucking a leaf.

Tuk.

The severed finger rolled on the silver tray.

"Now then, you said you'd pay with your body, right? Here's a down
payment of one finger. Not enough? Well, just one finger is indeed not
enough. Wait, just, snap."

And then, she snapped off another one.

There were two fingers on the silver tray.

"Two fingers. Ah. You said earlier that you valued loyalty, right? Right.
So, let's start with three for now. Here. Snap."

There were three fingers on the silver tray.

However, the bamboo hat was a well-worn assassin. He immediately
drew a dagger from his bosom and lunged it towards Qing's eye, only
for it to go flying with a crunch.

"Ah shit. I was surprised. I accidentally broke his wrist, you see? Don't
worry. It broke cleanly, so you can reattach it later. But."

Qing smiled eerily.

"Three is nowhere near enough, right? If you had just said so, instead of
suddenly resorting to violence. Did you really need that much more?
Huh?"

There were four fingers on the silver tray. Five fingers.

The bamboo hat swung his hand without fingers, splattering blood
everywhere.

"Now then, you two. Stop. What might this be? The answer is receiving
an order. It's sparkling, isn't it? Since you got the answer wrong, it's
penalty time. Drop your swords and kneel. Won't you?"

The two henchmen, who had drawn their swords but were hesitating
because the hand-to-hand exchange was too gruesome to watch,
dropped their swords and knelt upon seeing the faintly glowing, blooddripping white palm.

"Eueub!! Ueueub!!!"

"Stop blowing on me, it's ticklish. Ah, is it because your body isn't
enough? It can't be helped, I'll be generous. Six."

At that, the bamboo hat raised his right hand over his shoulder and
moved it away. It was the hand with the broken, dangling wrist.

Since Qing's left hand was holding the receiver's jaw, her right hand
couldn't reach the fingers still attached to the dangling hand.

Qing wondered what to do. She could remove the jaw, but then he'd be
able to scream.

She needed to switch her right hand to hold the jaw, but to prevent him
from screaming, she had to grip the neck with her right hand, but then
her left hand would, um, her right hand would.

Ah shit. Why are human hands only two?

However, Seol Yiri seemed to have an answer to that.

Humans have two hands so they can help each other.

Having suddenly stood up, Seol Yiri grabbed the dangling hand of the
man and twisted off the thumb with her other hand.

Ah. Is our Yiri over here? That's some quick thinking.

But look at her go.

She can't even snap off a single finger.

She twisted it up, down, left, right, and shook it, but she couldn't
manage to detach it.

Human fingers were surprisingly tough, with bones, tendons, and flesh
all intertwined.

"If you can't get it off, just use a sword. There's one you dropped
earlier, isn't there?"

"Yes."

And so, there were six fingers on the tray.

Five with rough cross-sections and one cleanly cut with a sword.

The cleanly cut fingers on the silver tray, adorned with droplets of blood,
were impressive.

It looked like some kind of modern art? The title could be, um, 'Tearing
Off vs. Cutting'.

"Look here. There are six fingers. How much more do I need to pay to
learn the identity of that assassin and where to catch him?"

"Eueub. Eueub!"

"Ah. It's ticklish, I said. From now on, if you blow on me, your body
won't be enough. Blink if you understand. What did I say?"

At that, the bamboo hat 열심히 blinked.

Qing finally released his jaw and wiped it on the man's chest.

Then she sniffed. Ah shit, it smells like spit…….

"How nice would it have been if you had just spoken nicely. Did you
really have to make me go through the trouble of paying with my body?
So, how about it? Do six fingers amount to twenty Gold Ingots?"

"Yes! Yes, they do!"

"Now then. So where is that bastard? Not just that one, but also the
other bastards who stabbed the master carpenters with their swords."

"Please, spare my life."

"Who said anything about killing? Tell me their details."

"That, I really don't know."

"What? But I thought you said it was worth twenty Gold Ingots earlier.
Are you selling something you don't have while overcharging? Wow,
that's really bad, isn't it? That's four fingers' worth of bad."

"Please! That guy trades with the Great Fortune, the Great Fortune
assassins' hideout! I'm just a low-level guy, how could I know the
identities of such big shots!"

"Eh. Then who would know?"

"Th-There, if you go out to the innermost area, there's a luxurious door
decorated with gold. The guy there is directly connected to the
assassins' hideout, so he'll know. He'll definitely know!"

"A luxurious door, huh? Will I recognize it on sight?"

"Yes! You'll recognize it immediately!"

"Hmm. But, this doesn't quite add up, does it? Here are six fingers,
which should be worth twenty Gold Ingots, but all I got was information
about a luxurious door with someone who might know. That's a huge
loss for me, isn't it?"

If Cheon Yuhak had heard this, he would have clicked his tongue.

To think she had become a robber instead of a thief.

And not just any robber, but a vicious one who tore off people's fingers
and treated them like her own money.

However, what could Cheon Yuhak do even if he saw this?

With her victory after receiving the teachings of the Divine Fist, Qing
was practically invincible.

Thus, the incredibly vicious robber, with the face of the Greatest
Beauty Under Heaven, smiled and spoke.

"Tell me everything you know. If the information is worth about twenty
Gold Ingots, I'll spare you."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Hm. Unfortunately, the information was worthless.

And promises must be absolute.

She had said she would spare him if the information was worth twenty
ingots, but it wasn't.

Well then. What should I do? I can't spare him, can I?