\chapter{Fire In Chang'an (16)}

That's basically saying if you have the guts, then try to report this.

Nam Moonseong flinched, then felt a chill.

When he thought about it, it really was so, thus his flinch.

And his heart sank at the ominous hostility that was trying to utterly exterminate his seed.

"You bitch! You bitch! What outrageous nonsense is this! You… you bitch!"

When he was lost for words, this was all he could say.

Ah shit. How do I endure this?

Qing was tempted by a great urge, but finally, she could not resist the impulse that suddenly surged up and she ended up answering.

"Whether it's two years or one year, please don't make it too long, but couldn't you immediately bring that so-called Lady, kneeling before me?"

"Keueum……"

Nam Moonseong desperately racked his brain.

He just had to get through this right now.

The claim that he was close to the Chief of the Capital Guards was true. In fact, his second son and the Chief's very ugly daughter, who had been a great concern of his, were to be married next year.

Anyway, this matter could be swept under the rug by getting rid of the witnesses and pretending to investigate for the authorities.

If he showed sincerity to the elders in Hanam by spending the gold he had obtained through the flood relief project and adding the existing family fortune, this mere incident in the small city of Naknyeong could be buried without any issue.

"Look here, I think there has been a misunderstanding."

"Oh really? And how is it that an old man like you knows that? Did you also take part in diverting the materials for the flood relief work? Oho. Now that I look at it, it seems that it wasn't just the Lady but the head of the clan who personally planned to submerge Naknyeong."

"No, it's a misunderstanding, a misunderstanding. Why don't we just talk this out, just the two of us, hm?"

If it was just the two of them talking, it was obvious what he would say.

Qing snorted.

"Hey, old man. I've spent over forty gold ingots1 on the relief project for Naknyeong. That was all I had. If I had more, I would have spent it all. You think I'm doing this to receive something in return? Don't even think about trying to gloss this over, just bring that bitch to me right now."

A gasp of awe spread throughout the crowd.

So she had poured her entire fortune into the relief project for Naknyeong.

They seemed to have heard rumors that an angel had appeared in Naknyeong, that a goddess had descended on the land of Naknyeong.

Of course, the bandits would feel very wronged.

However, since their lives were defined by being treated like shit by those they had robbed, they didn't have much to say about it.

"Do you not understand what I'm saying? Hey, old man. Did you leave your children's education to dogs or perhaps a picture book of copulation? I don't know about the other children, but your raising of a daughter has utterly failed. So since you have such a demonic bitch of a daughter, if you wish to preserve your household, bring her here right now."

"How dare you, how dare you utter such gibberish……! Do you know, do you even know who I am?!"

"Oh my. Are you going to hit me? Then come at me. Here stands a robber with a sword, so try hitting me with that great wealth of yours."

Qing taunted, turning her Sword Force on and off in a dazzling and obnoxious display.

If the amount of strength one gained was proportional to how much they were being looked down upon, then at this moment, Nam Moonseong would have instantly reached the level of the Greatest Under Heaven due to the intense rage he felt.

However, the sword was close and the law was close, but not quite as close. At least for a rich man like Nam Moonseong, the law was not far away.

Originally, the law was the scariest monster in the world for those who had nothing.

For those who had something, the law was like a loyal dog that would wag its tail, piss itself, and roll over to show its belly.

But there was a sword in Zhongyuan.

The sword that had reached right under his chin was beyond the reach of even the protection of the stern and vicious national law.

"Even so, are you not afraid of the aftermath?!"

All he could say was 'just you wait and see'.

Qing snorted and answered.

"Are you curious? If you're curious, why don't you become a Supreme Master too, old man? If you're a Supreme Master, you can probably do things like this. You know. Like, emit Sword Force and stuff. Then maybe your guts will grow a bit."

"Ugh."

Nam Moonseong staggered.

He felt like crying out of frustration and resentment, but-

"What's wrong, old man? Are you crying?"

In fact, he was shedding tears.

But Qing was relentless.

"Wow, everyone, can you see these tears? This old monster who devoured the lives of three thousand people is shedding tears because he's upset! If it weren't for you, if it weren't for the righteous heroes gathered here in Chang'an, no one would have known! These heinous crimes could have been well-concealed! All of this is thanks to all of you, the righteous heroes who lent your strength!"

"That's right!"

Devout followers immediately responded with shouts, and like a fire spreading through the crowd, a roar that shook all under heaven burst forth with a WAAAAAAH!!!

Nam Moonseong's mind cleared at that.

This wasn't the time to be swallowing tears.

His family's business was at stake, but more than that, his entire family was on the verge of extinction.

From the beginning, what Qing had demanded was the bitch of a daughter from the head family.

In other words, it was an offer to cut off the tail by obediently handing over the daughter.

But his daughter was a child he loved more than life itself. Among his children, she was his youngest and most precious daughter.

But what could he do?

Was he to let his entire family be exterminated without being able to save even one? Or should he hand her over and repay this grudge later?

After all, he was an old merchant who had climbed to this position by stealing and trampling on others. This was the decision he had come to.

"Listen, everyone! I'll be honest with you! The flood relief project was a business my daughter carried out alone, from start to finish. I swear to the heavens and to my ancestors, I did not help her with a single word, not even a single coin! We did this to ensure fairness when determining the successor of our merchant association."

The crowd looked at the head of the clan with suspicion.

"I know you may not believe me, but it is the truth. If there's anyone among you who does business with our association, you would know. Right now, each of my four children are running their own separate businesses!"

I do not know. The other children do not know.

It was all that daughter's doing alone.

And it was the complete, unadulterated truth.

He had already announced that he would hand over the association to the child who made the most profit by next year, as he was already halfway to retirement.

There was a murmur spreading here and there among the crowd, saying that was true.

How could the merchants of Chang'an not know about the affairs of the Jangheung Merchant Association?

Some were agonizing over which of the four they should side with, while others, believing that friendship was also first-come, first-served, had quickly picked one and stamped a friend's seal.

Those with the ability to hear could hear as much as they desired.

Hearing the murmurs, Qing thought.

I'm not sure if I believe it or not, but it seems like he really didn't know. He's saying it wasn't a tail cut.

Even so, with that level of Evil Karma despite not being involved at all?

What kind of vile life did he live?

It would be better for the world if he was just killed, right?

But Qing suppressed her killing intent.

A bastard who could be killed was not necessarily a bastard who should be killed, and if she spilled blood here, the crowd that had gathered could instantly turn into a mob of looters.

Qing knew the limits of the people of Zhongyuan all too well by now.

And if that happened, the blame for such atrocities would fall on her, who had led such a large crowd here.

Moreover…

The head of the merchant association was a bastard who should be killed, but there were quite a few innocent people among the guards who had their mouths agape, as well as the employees of the association who looked on with anxious faces.

Thus, a while later…

Finally, a woman who was being dragged by servants, struggling with both arms held, appeared.

And it was a dramatic meeting with that! very! daughter of the Jangheung Merchant Association.

"Let go, let go of me! How dare you, ack!"

Whether the servants let her go because she asked them to, or whether they let her go because they had carried her all the way here, anyone could guess the answer correctly.

Qing looked at the Lady.

She was an ordinary beauty.

Even if one saw her on the street, they might have given her a second glance, but since she had devoured three thousand lives, her beauty was not enough for her to have four eyes or two mouths.

However, her Evil Karma was in the four digits.

Hmm. She's around the same level as Eonyoung, isn't she?

Hmm. Then…

Qing frowned deeply.

Then doesn't that mean that bitch Eonyoung had devoured the lives of three thousand people at that time as well?

Did she also burst some kind of dam?

How can one-

"S-Sob, I'm innocent!"

A tearful voice interrupted Qing's idle thoughts.

Qing looked down with a cold gaze at the Lady, who was sobbing on the floor, or perhaps pretending to sob.

What? A preemptive strike? Tears first?

Is this evidence of my innocence?

Qing tilted her head slightly.

"Innocent?"

"There's been a misunderstanding, a misunderstanding! How could this girl dare to take private gains in a great project ordered by the gracious heavens? I definitely instructed them to make it strong and sturdy, even if it meant making a loss! I truly did!"

The crowd murmured.

The story was different, wasn't it?

Then whose words are true?

"That's different from what the head carpenters said, though? They said you gave the order yourself, that at least half of it should be diverted?"

"Slander! I have never given such an outrageous order! That's right! But, I do have a sin I must confess to all of you!"

What? Is this a sudden confession time?

As Qing was about to clasp her hands together, thinking that perhaps she had misjudged the woman, she suddenly remembered she had decided not to do that anymore and quietly lowered her arms.

Why? Because it was too comfortable.

If you just put your arms below your chest and let the lumps of fat on it rest, it was so light and comfortable that it felt like taking off the military backpack you wore during your service before your discharge.

But since it was also an incredibly embarrassing posture, she had refrained from doing so, telling herself she would get into deep shit if she made a habit out of it.

At any rate, Qing tilted her head and looked down at the Lady.

Let's hear what she has to say.

"Upon hearing the news that the dam had collapsed, I realized that the construction had problems. I found out that the carpenters, thinking I wouldn't know because I was a woman, had secretly embezzled the materials for their own personal gain. But I was just too scared, too afraid of the repercussions, so I mobilized assassins."

I have never taken a single penny from the diverted materials.

I even gave instructions to make it strong and sturdy, even if it incurred losses.

But the carpenters thought I was a fool just because I was a woman and diverted everything. It was all the carpenters' fault.

I found out later, but I was so afraid that this fact would come to light that I sent assassins after the carpenters. That is my sin.

I am guilty of abetting assassination, but I dare not to have schemed to cheat on a project ordained by the Emperor.

Honestly, Qing was impressed.

Wow. She's really smart, huh.

To think the daughter of the number one merchant in a province would have such a sharp mind?

But admiration was admiration and…

"Ah. I see. So, the innocent Lady, fearing that she might be implicated in such a heinous crime, ordered not to provide relief to the victims of the flood in Naknyeong, but to increase the price of grain fifty-fold and to lend it out?"

"I have never given such an order!"

"Then, even though the price was increased fifty-fold, you just ignored it? You were afraid you'd be a criminal because the dam burst, but when it came to the tragedy of three thousand lives lost, you're saying you just watched because it wasn't your fault?"

"That's…"

The Lady, startled, rolled her eyes anxiously before bursting into tears again.

"I was wrong! I didn't, about such, such sorrow, I was still young and my thoughts were short and foolish, so I made a mistake, I made a mistake!"

Wow. Look at this.

Crying first, appealing with tears, hiding the big crimes and throwing out the small ones instead, and now even saying she was young?

It was a textbook example of an excuse, a perfect set of a comprehensive gift package.

Yes. I've heard enough.

Then, Qing approached the Lady.

As a shadow was cast over her, the Lady, who had her head buried in the ground and was sobbing, or pretending to, slowly lifted her head at Qing's presence.

Qing responded by kicking her.

Her vigorous kick slammed into the Lady's cheek, causing a loud thwack!!!

White fragments of teeth flew freely from her mouth.

Perhaps, the teeth, unable to endure their owner's disgusting nature, decided to make an emergency escape from this bitch's mouth. 