\chapter{Fire In Chang'an (17)}

The sound of the crowd gasping.

A woman's tears were indeed a powerful weapon.

However, even such powerful tears could be countered, such as with tears shed by another woman or a fierce slap.

Tears were not really Qing's style, and she didn't want to bow down to this bitch, so she just kicked her in the cheek with the top of her foot.

Yeah. Hmm. That felt pretty good, hitting with my foot.

Satisfied, Qing raised her voice for all to hear.

"Hey. Why are you lying when it won't even work? Do you think these warriors here are fools? Do you take them for idiots? How dare you look down on a young lady who is in a succession contest for the position of the head of the Shaanxi First Trading Company, saying that the carpenters secretly embezzled funds?"

Of course, Qing was wholeheartedly mobilizing her brain to make the villain into a dick.

Nevertheless, a rather sharp deduction popped out, which would have surprised those who knew Qing as an extraordinary event.

But the reality was a bit different.

Since Qing had already decided who the culprit was based on their Evil Karma, all she had to do was deduce backward from the assumption that this woman was the culprit.

Originally, if you knew the answer, it wasn't difficult to calculate the process backward, so you could say that Qing was just freeloading.

There was no need to be surprised that she suddenly showed an intelligent side.

"Argh…!"

The young lady rolled on the ground.

"Hae-ah!"

At that, the head of the trading company urgently embraced the rolling young lady.

Only then did Qing realize that she didn't even know the name of the young lady of the Jangheung Trading Company.

But what? Did she really need to know?

"What are you doing! What did this child do wrong to…!"

"Should I remind you what she did wrong?"

"It hasn't been revealed that my daughter did anything wrong yet!"

"Do you really think so? Honestly, haven't you known until now what kind of bitch your daughter is?"

"There is no such law in the world! There is no evidence yet that our Hae-ah did it on purpose!"

"Are those things you brought not evidence, but plaintiffs of evidence or something?"

"Those bastards are lying to save themselves-"

Thud. Qing lightly stomped the ground, cutting off the old man's words.

"Stop. I wonder how you educated your daughter. I'm sure you didn't teach her to be truthful or righteous. You must have told her to deceive, exploit, and that those who suffer are fools, to be smart and live by taking advantage of others. Isn't that why things are like this now?"

Of course, Qing didn't deduce their family's style of upbringing by evaluating their character with amazing insight.

This was just what the chaebol chairmen in the screens of Qing's hometown said to their children.

"Just think of it as receiving heaven's punishment. If you hadn't done this, you would have been struck by lightning anyway for having devoured three thousand lives."

As Qing said this, she roughly grabbed the father and daughter, who were clinging to each other, and pulled them apart.

It seemed that even though they had accumulated so much Evil Karma, they still cherished their daughter. When she pulled them apart, they clung to each other again, and when she pulled them apart again, they clung again, and the wrinkled hands struck her, creating quite a commotion.

"Let go, let go!"

"Daddy!"

They are subhuman, but their affection for each other is quite touching.

However, no matter how much two commoners hugged each other, how could they possibly win against the monstrous strength of a Transcendent Realm Master? No, even if she wasn't a Transcendent Realm Master, she still possessed the strength of Xiang Yu, so there was no way they could win.

Eventually, the old man was thrown aside, and the daughter was dragged out by her hair.

Even in the midst of this, Qing gained a great realization.

She wondered why everyone grabbed people by the hair, and after trying it herself, she realized there was no better handle than this.

"Agh! Let go! Let go, I said! Argh!"

"How can you be in pain already? What will you do later? The people of Naknyeong will want to boil their enemies alive. Or maybe they'll do something even more terrible. It's a bit of a relief if you die cleanly. As a fellow woman, I feel sorry for you, but, well, you must have taken that into account when you started your business, right?"

At that, the young lady's struggles intensified.

But what could she possibly do?

Then, finally, a desperate cry burst out.

"Why are you doing this to me! Everyone does it! When you get a business from the government, of course, you have to take at least half! Otherwise, you're an idiot!"

It was a cry that contained a hundred percent pure, genuine sense of injustice.

Angry murmurs spread among the crowd.

It was practically a confession.

The young lady wasn't stupid for saying this.

Originally, the last cry of a villainous creature was always like this.

I'm not the only bad guy, there are worse ones out there, so why are you only doing this to me? Everyone lives like this, so why am I the only one being treated unfairly?

The infuriating part was that they were genuinely aggrieved when they said this.

It was a natural characteristic of scoundrels.

"So? Let's say everyone does that. Let's say they do. If people were massacred as a result, shouldn't you obviously take responsibility?"

"I didn't know! I didn't know! Who would have known it would rain so much!"

"If you don't know, does that absolve you of guilt? Just accept your fate and die peac-"

"What gives you the right! What right do you have to talk about heavenly punishment!"

Qing paused, then sighed.

Well. Yeah. It's not really heavenly punishment.

Strictly speaking, it should be called Qing's punishment.

Hmm. It suddenly feels tiring……

"Whatever. If you have the energy to scream, you should think about the excuses you'll make to the people of Naknyeong. It's not like making excuses to me will suddenly change my mind and make me let you go."

"No, save me! Please, I……"

Anger, denial, and then supplication.

What was it again? The five stages of grief?

Wasn't denial supposed to come before anger?

But well, there's no way to find out……

With one hand holding the young lady's hair, Qing shouted.

"Alright, everyone. This criminal will be sent to Naknyeong so that the victims can judge her directly, allowing them to at least somewhat relieve their resentment."

Qing bowed deeply.

Alright. Now it's over. I caught the young lady, and the old man will probably live long if he's angry, so?

But for some reason, they just stood there, blankly.

The gazes looking at Qing were clear, as if they hadn't reached the end of the story where the credits roll.

Hmm. Should I… say something cool?

After thinking for a moment, Qing voiced the opinion of Ximen Qing, an individual.

"Everyone! Did you hear what that old man said? How dare… you… What right… What is he talking about? What is it about a merchant that makes him so noble as to dare to use such words! Is that decrepit old merchant your master, and ours?"

"No!"

"No, he is not!"

"When a merchant is humble, they greet guests with smiles and flattery, but when they become wealthy and handle gold and silver, they change their expressions and look down on you, saying they can't associate with you because you're dirty and lowly beggars! Isn't that right?"

"That's right!"

"That's exactly it!"

"Who made the greatest trading company of Shaanxi build such a huge manor? Was it that old bastard who fell over there? No! Isn't it purely thanks to the patronage of the warriors of Chang'an here? Isn't it the gold and silver contributed by all of you, the people of Chang'an, Xi'an, and Shaanxi, that built this huge manor?!"

At that, the eyes of the crowd widened.

It was because it was a revolutionary way of thinking that they had never heard before.

It was the reversal of the worldview, made famous by a certain Master Geo from the West, known for his technique of turning heaven and earth upside down.

This was because the ideology of people as the foundation of a nation had not yet properly emerged in the primitive, ancient, and uncivilized Zhongyuan.

Of course, there were ideologies that could be considered early forms of such thought, but they did not deviate much from the level of a virtuous cycle.

It only reached the level of 'If the ruler is like a beast, overthrow him'.

This was because, fundamentally, in Zhongyuan, the term 'common people' referred to weeds, something insignificant, not particularly useful, and only numerous in number.

In the uncivilized, primitive, and barbaric Zhongyuan, an individual was considered foolish, selfish, stupid, and evil, practically a complete piece of shit.

If the world were filled only with these pieces of shit, it would obviously become a living hell made of only blood and tears.

Therefore, heaven sent down rulers, and the Son of Heaven was the only person among these pieces of shit who was qualified to be a ruler.

In other words, the Son of Heaven in Zhongyuan was a being who 'bestowed' governance, the most precious and valuable grace in the world, upon the common people.

The state did not exist for the common people.

The state existed for a greater value, the order of the world.

And the common people were merely useless components, always eager to disrupt the order with their bloodshot eyes and cause trouble.

This was why the common people in Zhongyuan were always powerless.

But now, someone had appeared, shouting that it was because of everyone here that a merchant with such authority, someone they couldn't even dare to look in the eye, had grown so powerful.

That it was their money that had created his wealth and power.

The shock to the crowd was immense at hearing this.

"Huh? Is that so? It does make sense, doesn't it?"

"That's true, isn't it?"

"Thirty years ago, Jangheung Trading Company was just a small fabric shop over there in the corner. Back then, the owner was friendly, and the quality was good, so the neighborhood people trusted him and bought from him. Yeah. In thirty years, customers have become mere 'you people'."

If it had stopped there, it would have been fine, but Qing added a vicious incitement.

"So, from now on, if there is such tyranny, even if it's not me, you, the warriors who hold justice in your hearts, should step forward! If there are no customers, can any trading company, no matter how large, survive? If you don't buy such evil trading company's goods, don't mention them, and stop trading with them, what can those bastards do?!"

Once again, a shock swept through.

Of course, Qing's origin was a class society that advocated for the equality of all people, and if anything, Qing's class was just above the poor, stuck at the very bottom.

Thus, Qing's perspective of looking from the bottom up was always sharp, venomous, and extremely biased to one side.

"And not only that! You can also stop interacting with the houses that trade with Jangheung Trading Company. If someone uses Jangheung Trading Company's goods, you can inform them of the truth and make them aware of how shameful it is. And if they still use them, you can spit on them and insult them, using all your might to prevent anyone in the world from giving gold and silver to such cannibals. That is what all of you can do, as you are not servants of that old man, but benefactors who helped him achieve this power!"

Qing was listing all the nasty things one could do.

It was a huge shock to the crowd.

Wait, there was a method like that?

And then, waaah!!! A huge cheer erupts.

They were responding to and praising the great ideology that transcended the era.

However, Qing didn't really know what she had said.

Because in Qing's hometown, such things were considered common sense that anyone would naturally assume.

Of course, the radical boycott, saying 'You have the right to interfere!', wasn't exactly common sense, but rather just Qing being a bit of a troublemaker adding her own twist.

However, since the merchants of this era were fundamentally different scumbags compared to those of the modern era, it could be said that some allowances could be made.

After all, this was an era where the law of the land came from one person's head and where being good at following it was considered idiotic.

Even though Qing had been in Zhongyuan for five years and was now a proper member of society, she still hadn't quite outgrown her hometown roots.

Originally, humans were beings that could not easily escape the roots of the society in which they spent their formative years.

Thanks to this, here, in a street of Chang'an, which was once the center of the world and is still used in the term to refer to the center.

The power of consumers (bullying), which transcended the era, had revealed itself.

It was also a spark that could potentially become a terrible flame, capable of burning down the era if mishandled.

It was also golden words personally bestowed by a princess, whose bloodline was considered to be from the heavens.

But Qing didn't know.

After all, she hadn't made such a statement with the mission of enlightening the people with the spirit of the times.

She just said whatever came to mind because it felt awkward to end it as it was and everyone seemed to be expecting something more.

So she just thought, 'Wow. I really wrapped that up well.'.

And so, with a bright smile, she held tightly onto the hair of the young lady, whose face, after being kicked, had swollen up like a bun.

By the way, in Zhongyuan, when they said 'bun', they meant the kind of food that was deep-fried in oil with an empty inside, similar to what was called 'empty bread' in Qing's hometown.

The food called 'bun' in Qing's hometown had a separate name, 'steamed honey bread', so.

With that in mind, Qing thought.

Hmm. I suddenly want to eat a bun. Both the hollow and the steamed honey kinds.
