\chapter{Fire In Chang'an (3)}

The city had almost been restored.

Of course, it would never be the same as before, as many lives had been lost.

However, the mere fact that the damage had been repaired to this extent in just one month was a great feat in itself.

Of course, the Heavenly Maiden, who always flew around as if she knew no idleness, had a significant contribution to this.

Since the Heavenly Maiden was working, others couldn't just play around. 'She's indeed divine, but couldn't she work a little less strenuously?' they thought, as they were forced to move.

So, in just one month, the ruins had almost disappeared and houses with makeshift roofs had taken their place. The blood and sweat shed during this month would become a great historical achievement that the people of Nakgnyeong would be proud of for generations to come.

"Aigo. What's this? Just when I thought you were finally going to study properly. Where are you going?"

"Well, Elder? I'm not originally a physician, am I?"

"Tch. If you've learned medicine and tended to patients, aren't you a physician then? Here. Keep this with you and memorize it in your spare time. I'll ask you later if you've memorized it all."

"No, but where would later be?"

"Hmph. Who knows what the future holds? You're a woman with quite the wide connections, so we're bound to meet somewhere."

The Grand Physician clicked his tongue and thrust a medical book into her hands.

In truth, although the Grand Physician didn't say it, he was surprised at the speed at which Qing learned medicine.

Originally, medical books were full of difficult terms, so when reading alone, one would naturally encounter parts they didn't know or understand and would have to ask questions.

However, since she never asked him even once, he thought that perhaps this girl wasn't even looking at the medical books. But when he asked her questions, she answered them right away.

There was a fact that the Grand Physician was unaware of; that Qing was already a master of human anatomy, one of the best in the martial world.

She already had a clear blueprint in her head of what the human body looked like, how the muscles, tendons, and blood vessels extended, and how the internal organs were shaped and connected. As such, her comprehension of the medical texts was a hundred times greater.

Of course, the Grand Physician, unaware of this fact, thought, 'Ah, she has an outstanding talent. It's a waste, so I should give her at least one medical book'.

If she had been a man, he would have followed her around and raised her to be a proper physician. But she was born a woman, and the heavens were truly heartless.

No matter how skilled a woman was in medicine, she could only be a female physician at best, not a proper, fully recognized doctor.

The once-successful Grand Physician suddenly found himself becoming an average man of Zhongyuan. But what could he do when that was how the world perceived things?

In fact, considering that he was an old man with outdated views, the act of handing a medical book to a woman could be considered enlightened.

If it were Ximen Surin, she would have thought this and pulled out all his beard, but Qing had no such thoughts.

She had just learned from a respected elderly physician who had helped people all his life.

Then, caught up in the atmosphere, she somehow ended up becoming something like an apprentice female physician. But in the beginning, Qing was a martial artist, not a physician.

"All is good, but abandon that ambition of yours. Every time you do something, you make a show of it. Do you really have to shout out, 'This Ximen Qing will help', emphasizing your name so?"

"Ah. Well. I have my reasons for that."

In fact, those words were what Qing had been saying all the time while helping with construction, distributing grain, and working as a female physician.

'This Ximen Qing will provide', 'This Ximen Qing will especially check your pulse', 'This Ximen Qing has built houses one, two, three, four…….'

However, Qing did it on purpose to show off, and yes, it was indeed to show off.

Why, you ask? It was because she had unfortunately missed quite a few bandits.

It would have been great if she had killed them all and not let a single one escape, but she couldn't handle it alone when the vermin scattered in all directions.

That useless Seol bastard was too busy getting beaten up by bugs to be of any help.

Moreover, she had even left the young master's corpse out in the open.

It was an already determined future that those Green Forest bastards or whatever would be furious and seek revenge.

So, she had been revealing her name all over the place, just to let them know that their enemy was here and not to bother innocent people.

If Qing had known about the Green Forest, she would have at least hidden the corpses by throwing them off a cliff or something.

But Qing couldn't even comprehend that there was an official group of bandits known to everyone in the world.

Moreover, the bandits Qing had encountered were just those ridiculous guys who disappeared as if time had been turned back when she said, 'If I'm a Master, then-'.

Honestly, she looked down on them.

If those bandits are going to make a fuss about revenge, wouldn't that just be rolling in more bastards to kill on their own?

They're coming to me even though I'm just standing still? What's not to like?

But I can't let them harass other people just because I like it, so I have to shout out that it was me.

Anyway, thanks to that, something akin to a faith, no, just a Heavenly Maiden faith had emerged in Nakgnyeong.

This was thanks to the efforts of the Heavenly Demon Cultists of the Taecheong Emporium, who worked hard to spread the word.

Roughly speaking, it was a doctrine of the Heavenly Demon Divine Cult, twisted to resemble the Maitreya faith, about a Heavenly Maiden who would lead the gathered followers to a new era when the world shattered and collapsed in the distant future.

Although it wasn't Qing's intention, it was a heinous act of laying the cornerstone, a large pillar, and a solid bridgehead for the Demonic Cult's evil plan to conquer Zhongyuan through their influence.

Perhaps as a reward, Qing's Righteous Karma had also increased significantly.

Helping an evil plan and also gaining Righteous Karma, how cunning and wicked, am I right?

"Aigo, Young Lady. When will I ever see this dazzling, radiant beauty again? This old man, Geoltaran, understands now the pain of having one's heart torn to shreds."

"Ehh. Anyway, thank you. Thanks to you, I was able to rest comfortably? Um? Did I rest comfortably?"

Come to think of it, she hadn't rested comfortably.

Because of the flood, they didn't eat precious dishes-

It wasn't that she couldn't eat them, but rather that she chose not to. After all, Geoltaran had offered to hold a banquet every morning, noon, and evening, but Qing had refused, saying she couldn't indulge herself in such times.

-she woke up before dawn and worked on construction, tended to patients, and took care of Seol before studying medical books late into the night before going to sleep.

Of course, the bed was soft and of the highest quality, so at least she slept well thanks to the comfortable bedding, despite her fatigue.

"Anyway, thank you for treating me like a high-ranking guest when I suddenly appeared out of nowhere."

"Huek, keueup."

At that, Geoltaran finally failed to hold back his tears.

"No, why are you doing this again?"

"This lowly one, to be graced with such an undeserved honor, sob, thank you, thank you again…"

Geoltaran was great in many ways, but he was a bit strange.

He had been sniffling at every word of thanks for the past month, so Qing just thought he was a strange person and-

This was how scary it was to get used to something. Even though it was strange, she just accepted it as how he was, rather than wondering why it was strange.

"Huu. Hoo. If you go to Chang'an, you may stay at the Sunrise Inn."

"Sunrise Inn? Is it also related to the elder?"

Geoltaran gave a prepared answer.

"It's not like that. How could an Emporium operate alone? Since the Taecheong Emporium doesn't have an independent distribution network yet, we have a contract with the Sunrise Inn, making us practically sworn brothers. So if you go to the Sunrise Inn, they will treat you like a VIP."

"Oh. Well, I guess that's good."

What did Qing know about the matters of an Emporium?

She knew nothing about other things, let alone the Emporium's business.

Since they were practically sworn brothers, she just thought of it as a friendly inn.

To be fair, with a name like Sunrise Inn, it sounded overtly like the Heavenly Demon Divine Cult.

But Qing didn't know.

Whether it was the Sunrise Divine Cult, Cult of Fire Worshippers, Taiping Daoist Sect, or Heavenly Demon Divine Cult, she didn't know any of them.

She wasn't even curious.

And so, as Qing was about to depart, all the residents of Nakgnyeong gathered to see off the Heavenly Maiden on her way.

The carriage had been upgraded to a very luxurious one, and among the horses harnessed to it, the one with the familiar-looking left rump was that smart one from before.

As such, Qing sat down, and Seol, naturally, took the seat next to her.

Huh? Why is she coming to my side?

Seol's purpose was very simple.

It was now mid-August.

The heat was at its peak, making it scorching hot, and Seol was one of the people in Zhongyuan who suffered the most from the heat.

Since even the coldest days in Zhongyuan were similar to the warmest days in the North Sea, the hot days in the Central Plains felt like being trapped in a sweltering steam bath for those from the North Sea.

But Qing's hands were cold.

Seol wiped the waterfall-like sweat from her forehead with Qing's hand, wrapped her hand around her own wrist, and then placed it on the nape of her neck.

It was the image of an Orthodox Faction female expert (though useless) enjoying the cooling effects of the White Hand Demonic Arts.

However, while it was cold for Seol, the touch naturally felt hot to Qing.

Qing was about to say something, but then she thought about how hot this poor kid must be to do this.

She was sweating so much that it seemed like there was a person or a fountain in the garden. Seriously, if you gently tapped her, you would hear a 'splash splash' sound.

"Hey. If you're so hot, why don't you use your Ice Arts……"

"I must prepare for an ambush."

"Eh, the person driving the carriage works for the Taecheong Emporium, you know? Just relax and circulate your Ice Arts."

"I can't."

Qing immediately gave up on persuading her.

This kid has a stubbornness made of iron.

Am I the one who's suffering? It's her.

Even though she's suffering so much from the heat, she refuses to use her Ice Arts to conserve energy, saying she has to protect me.

Well, they were touching words.

Of course, with her skills, she wouldn't be able to protect anyone and would just get beaten up. But still, the thought was commendable.

Thanks to the Blissful Maiden Arts, Qing didn't feel the heat much, so if she just opened the window and let the breeze in, um. It's a hot breeze…….

It would be a bit cooler if I used Ice Arts too. Huh?

Then, a question suddenly occurred to her.

Wait. Why don't I feel cooler when I use Ice Arts?

"Hey. Why are you cool when you use Ice Arts? I don't get cooler when I use them."

"It is the Cold Heart Arts."

"Cold Heart Arts? What kind of martial art has such a pathetic name?"

"Yes. Yes."

Qing's informal speech came naturally.

Seol had gotten used to it at some point and accepted it quite naturally.

The Cold Heart Arts was the survival technique of the people of the North Sea.

To be frank, the Ice Palace was not a place where humans could live.

Even the residents of the North Sea didn't live on the ice.

They lived on the tundra, and when winter came, they moved south. When the weather warmed up a bit, they returned.

But the bastards of the Ice Palace lived on the ice all year round.

It was a basic technique for North Sea martial artists to endure the cold.

Originally, it wasn't used to cool down, but rather to regulate body temperature to stay warm and avoid freezing to death.

To use an analogy from Qing's hometown, it was like bringing a refrigerator to the North Pole, where the inside would be warmer than the outside.

"Hmm. It's Blue."

At that, Seol looked directly at Qing.

It meant, 'What are you talking about?'.

Qing just ignored her gaze as a response.

It meant to mind her own business.

"But it sounds good though……."

"Shall I teach you?"

"Huh? Can you teach me that?"

"Probably."

It was an uncertain answer.

"What do you mean, probably?"

"Everyone learns it."

"Can you be a bit more specific?"

In the North Sea, they considered themselves martial artists, so they called themselves the Martial Artists of the North Sea.

It was a statement that made people of Zhongyuan snort.

How dare they call themselves martial artists when there are only a few sects gathered there?

Anyway, in the North Sea, there were several sects besides the Ice Palace, and among them, there wasn't a single one that didn't learn the Cold Heart Arts.

So it wasn't really an Ice Palace martial art, nor a North Sea one.

In the first place, besides the function of warming up, or cooling down in Zhongyuan, it was a very poor cultivation method.

There was almost no increase in Inner Qi.

Even if the realm was high, the output of the Ice Arts was lukewarm, so the original power of the Ice Arts wasn't there.

It was just a necessary life skill, close to a survival technique.

"Hmm. Then, teach me. The cultivation method and all."

"Yes. Yes."

Seol obediently taught her the mantra and cultivation method of the Cold Heart Arts.

Qing sat in the lotus position accordingly-

"Wait, can you let go of my hand for a second? If you're really hot, just use the Cold Heart Arts for a bit."

"Yes. No."

Thus, Qing acquired the Cold Heart Arts!

Since it had a Blue Border, she easily raised it to Seven Stars, and she could feel a tiny, miniscule amount of Inner Qi settling in her dantian.

The Inner Qi Cultivation Method seems to be garbage. I guess that's true.

Qing tried to circulate the True Qi as a test.

However, thanks to the effects of the Yijin Cleansing Method, Qing's meridians and even the smallest of her capillaries throughout her entire body were as wide and sturdy as a two-lane highway.

As such, even the meager True Qi was amplified by the Jade Maiden True Qi and the Ice River Demonic Qi, thus allowing her to practically become a human air conditioner. Cool air gushed out from her entire body.

"Haeuuu……."

A moan of pleasure escaped her lips on its own.

The cool air seeping into her clothes was, woah. My goodness. I really don't want to say this, but it almost feels like I'm about to cum…….

And there was one more person who couldn't resist.

"Hauu……."

Seol clung tightly to Qing's side.

It was hot and damp, so at first, her annoyance spiked.

Qing's eyes narrowed.

"Hey, just use your Ice Arts, okay? I'm hot too, you know?"

"I can't."

"No. Come on. Why? You're going to save up on Inner Qi and do what with it?"

"I will protect you next time."

So, the sound of her reply was, um.

Ah, this is a bit touching, isn't it?

It's like that program, Our Child Has Changed?

To think she was desperately enduring the heat to save Inner Qi, saying she would protect Qing.

Of course, those words were touching.

But with her skills, rather than protecting, she would just get beaten up. Still, where else could she find such a thought?
