\chapter{Fire In Chang'an (1)}

The amount of grain that Qing had purchased at double the market price was enough to last comfortably until autumn.

The city was originally a distribution hub along the Luo River, so there were many warehouses in the area.

Since warehouses in good locations in Luoyang were already expensive and full, goods with low value-to-volume ratios, such as grain, had moved to Luoning.

However, there was a fact that Geoltaran had not mentioned.

The city's population had decreased significantly.

The flood control construction was completed in spring, and people were living in peace, trusting in the newly built levees and embankments.

However, due to that trust, a massive surge of water had breached the walls, and the levees, unfortunately, burst in the middle of the night.

As a result, entire families were swept away, leaving no one to even hold funerals, and even if there were, houses were destroyed, people were trapped, and drowned. The scale of the damage was already impossible to estimate.

But to tell the Heavenly Demon Supreme, who was taking on the resentment of the people for the sake of the innocent, that there was enough to eat for a long time because the number of people to feed had decreased significantly, would not be appropriate.

So, Qing just asked casually.

"There's that much? We didn't have to go around to all those places, then?"

"Oh no, Young Lady. You have made a very wise decision. When a city suffers from a flood, merchants from all over the world come with their eyes bloodshot, ready to take advantage of the situation."

When a flood occurred, grain prices in nearby areas would rise simultaneously as if by agreement.

In fact, it was indeed by agreement.

It was a secret meeting of merchants who conspired to raise the prices, so they would naturally increase dramatically.

Then, when those from the flooded areas came to buy, they would sell at inflated prices, and when selling in their own towns, they would claim that since those from the flooded areas were sweeping everything up, there was a shortage, thus overcharging.

In an instant, the price of grain would increase tenfold, and people would grit their teeth while cursing that those who should have drowned properly were causing trouble in other towns.

The hatred was directed at the poor victims, not at the merchants who were raising prices while pretending to be pitiful.

However, by stockpiling enough grain to last until autumn, the nearby merchants had no excuse to raise prices, and the people of Luoning would not be unfairly criticized.

"Hah. Merchants are all the same, can't trust a single one of those bastards."

But there was nothing to be done.

After all, in order to succeed as a merchant, one needed the heart of a vicious, evil scoundrel.

The ability to trample on others without any remorse, to laugh as they took the last coin from the battered and weeping victims; only a bastard under the heavens could possess the qualities of a great merchant.

As such, Geoltaran deeply engraved the words of the Heavenly Demon Supreme into his heart.

Of course, he didn't plan to keep it to himself.

Before the year was over, all agents of the Heavenly Demon Divine Cult's secret operations in Zhongyuan would have these words engraved in their hearts.

Since this is the will of the Heavenly Demon Supreme, merchants are nothing but sons of bitches who can be beaten and tortured without any issue.

Later, when a new era dawns, they will become the most despised of all professions.

"Hmm. Did you receive the roster?"

"Yes, I did. However, since it is more of a daily wage payment list than a proper roster, I'd say that at least half of the names are not actually present."

The 'not actually present' naturally referred to people who were only on the daily wage payment list but did not actually exist.

Anyway, according to the official records, they officially worked, so their daily wages were officially paid.

However, it was unclear how the wages of the non-existent people were collected.

"It's really leaking gold and silver like a sieve. I don't know how they can keep finding more rot no matter how much they dig. But, ugh, this is so bothersome……"

Qing scratched the back of her head.

Then, Geoltaran smiled very brightly and asked with enthusiasm.

"Oh my, Young Lady! Bothersome, you say? You can just order us, the servants of the Qingshang Bang, to do such tasks!"

"Oh? Why should I order around members of the Merchant's Association when I'm not even a part of it?"

"Well. That. If Lord Choi ever found out, how terribly would he scold us! He specifically instructed us to provide you with every convenience!"

"But an old man is an old man, and I am me."

"And me! This lowly one gets incredibly anxious if there is no work to do, so please, if there is anything to be done, let this lowly one do it! That is the only way this lowly one can live!"

It was a cry that contained a powerful will to do whatever it took to be given tasks.

It wasn't just words.

His eyes were sparkling, almost as if he was a dog who had heard the word 'walk', overlapping with such an illusion.

After all, this was an opportunity to carry out the direct orders of the Heavenly Demon Supreme. How could an agent of the secret operations, who had been thoroughly brainwashed from a young age to serve the Heavenly Demon Supreme as the sole purpose of his life, pass up such a chance?

With such a desperate look, Qing thought…

Well, if he's going to be like this, I might as well make use of him.

"I heard from a waiter last time that the technicians mobilized for the construction don't seem to be the type to run their mouths. So if you ask the laborers, you'll probably get all sorts of information about those technicians, like their names, what they do, and so on."

"Ah! If it is such a task, you must leave it to this lowly one! Since people are flocking to the city for relief, it will not be a difficult task to ask around at this time."

"Oh. As expected. You really need to have a knack for these things to solve them easily, huh? Right?"

"H-Huhu. Thank you, thank you. It is an honor of a lifetime, a joy that I will cherish forever, no, even in death, I will not forget."

Qing snickered.

This old man really hams it up whenever he gets even a little bit of praise.

Is it because that old man doesn't praise him often?

Well, I guess the old man can be like that.

"But do you think there was a problem with the flood control construction?"

"The designer said there were no issues with the design."

He had even emphasized that it should have withstood this level of rain without any problems, so there had to be a clear reason why the disaster still occurred.

"Anyway, we're on our way to Mount Zhongnan. Since the head merchant of the Changxing Merchant Association is in Chang'an, right? We might as well stop by and if there's a problem, um. Well. Yes. What can I do about it, but still, since I found out, I can't just ignore it, can I?"

Qing grinned, a thick smile spreading across her face.

"If something happened, someone has to take responsibility."

And in Qing's eyes, a color that did not exist anywhere in the world quietly flickered with an ominous light.

At this, Geoltaran's eyes also began to glisten with tears.

The Heavenly Demon Supreme is overflowing with a divine wrath and majesty that is akin to the end of the world!

Such a fearful dignity!

Heavenly Demon Supreme, my soul's eternal owner!

Meanwhile, a high-speed dispatch from the Divine Cult's secret operations flew like an arrow.

[The Honored Guest is heading to Chang'an.]

The recipient was the head of the Taiching Merchant Association, Choi Leeong.

The destination was the Seol Family Merchant Association in Zigui County, Hubei Province.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Geoltaran said he would take care of everything, so she should rest well while he investigated.

He was practically shooting desperate gazes at her, begging her to stay.

Since she needed to find out about the key technicians involved in the construction anyway, well, she had to stay, what else could she do?

He said they would hold a banquet in the evening, but seeing how the city was in this state, what kind of banquet could it be? She told him to just keep it simple with plenty of food and returned to her accommodations.

There, she planned to take a bath, change clothes, grab Seol Ri, have dinner, and rest well.

So, she entered the most exalted room in the merchant association building… wait, why is the name of this guest room so grandiose?

Of course, in Zhongyuan, large manors typically had a best room and a second-best room for guests.

After all, it was only natural to differentiate between guests based on their status.

At the very least, it was a matter of common courtesy and etiquette to treat the most honored guest and the next most honored guest differently.

Therefore, the best guest rooms were usually given somewhat grandiose names.

The Wulin Alliance had the Celestial Martial Hall, and even the Divine Maiden Sect had the rarely used Peony Blossom Hall, which had become more like a storage room.

But what's with this 'Most Exalted Room in All of the Three Thousand Worlds'?

Wasn't excessive courtesy impolite? After all, if the courtesy was excessive, it would only make the guest feel uncomfortable.

Of course, Qing was unaware that this grand guest room existed for only one person in the entire world.

And since she knew nothing about anything else, how could she know the facts that were not told to her and kept hidden?

Anyway, the Most Exalted Room in All of the Three Thousand Worlds was much wider on the inside than it appeared from the outside.

What did this mean? It meant that in preparation for a visit from the Heavenly Demon Supreme, detachable walls had been installed. By removing them all, an entire building was turned into a single room, making the interior much wider than the exterior of the room appeared from the outside.

And there, a luxurious and precious bed was placed, upon which a woman was curled up, turning her head to look at the sound of the door opening.

"You're here."

Qing's eyes widened.

What? What did I just hear? Was that an auditory hallucination?

Did Young Lady Seol just greet me first? For real?

It was an unimaginable welcome.

"Young Lady Seol. Are you feeling any better?"

"No……"

"No, I mean, you should have gone to see a doctor instead of just saying no, eh? Did you just say no?"

"Yes……"

She was sweating profusely, looking very much like a patient with a serious illness.

Since she had been sweating like that in the carriage, Qing thought it was just because of that, but it seemed her condition was actually quite severe.

"Ah, shit. I told you to get it checked earlier. Just wait a bit. I'll bring a doctor."

Thus, a doctor who looked like an immortal examined her and said-

"Tsk tsk, how could someone, a woman at that, be treated like this? But it's also strange. In all my eighty years of life, I've never seen someone injured so well."

The aged doctor clicked his tongue as he spoke.

But wasn't there something a bit strange about what he said?

So Qing asked.

"Injured well?"

"Yes. Well injured."

"No, I mean, if you're injured, you're injured, but what do you mean by injured well?"

"Hmm. Well, there are usually two cases."

Either the attacker had technically beaten her evenly, avoiding critical points and permanent damage.

"Or the one who was hit was skilled at taking a beating, so that despite being hit, they avoided getting any broken bones or serious injuries, thus preventing any permanent damage."

"Getting hit well is a thing? It exists?"

"Of course. Look at those beggars. They get beaten to a pulp, but after a while, they're fine as if nothing happened. It's all about experience. If you get hit every day, you learn how to take a beating."

"Ah. That."

When it came to getting hit, Qing was also a skilled expert who wouldn't be outdone by anyone.

So being good at getting hit was a thing.

But would Young Lady Seol, who was practically the princess of the North Sea, have ever been beaten?

Since she wouldn't have learned how to take a beating, that meant the bandits must have beaten her meticulously.

After all, they had said something about needing to save her to offer her to some young master and had beaten her without using weapons.

"Um. So, is she okay?"

"There are fractures. All over her arms and legs, too. But she'll be fine with rest. Apply medicine and she'll heal. Take medicine and she'll heal even faster. With how well she was beaten, there's not much to examine."

Was he really a skilled doctor?

He sounded a lot like a quack.

However, since Geoltaran had found him, he couldn't be a quack, and given that he was still spry at over eighty years old, it seemed his accumulated experience alone would make him a renowned physician.

"Um. So she'll be fine with rest?"

"Yes. Ah. By the way. I heard the Young Lady is starting a large relief effort? Then, could this old man ask for ten gold coins?"

"Huh? Suddenly?"

"Right now, the city is in chaos because houses have collapsed and there's not enough food. It would be a miracle if they don't all die from starvation. In times of disaster, do you know what comes after? Plagues. So we need to quickly gather the corpses, perform last rites, give medicine to those who are sick, and make them well before their conditions worsen. But all of that costs money, doesn't it?"

"Ah. I see. Geoltaran, how much gold do we have left? Is it more than ten coins? Give it to this doctor, Elder-."

"Ahem. Tsk tsk."

The doctor cut off Qing's words and clicked his tongue.

Qing's voice was filled with injustice.

"No, why? I said I'd give it to you."

"No, if you just give gold to a doctor, do you think medicine will just sprout from the ground? Even if medicine sprouts, who will prepare it? We need to attach people to the effort. How can this old doctor do it all alone?"

"Ah."

She hadn't thought that far.

"Geoltaran. This Elder says he wants to provide medical services to the city. Can the Merchant Association help? I thought about food and rebuilding, but I didn't think about this."

"Oh my. Young Lady, you do not need to ask, just command us. Do you think we would dare to refuse anything the Young Lady says? Even if you told us to jump into a fire with firewood on our backs, we would obey."

It was a terrifying statement, to say they would die if ordered to, but with his unique sycophantic tone, it had no persuasive power at all.

So Qing just laughed it off.

After all, Qing didn't have the ability to read minds. 