\chapter{Fire In Chang'an (13)}

Qing found it hard to believe that a notorious group of assassins, a
veritable organization of scoundrels, could actually survive and thrive.

Not just any group of assassins, but a famous one.

In fact, it was common for a nation to operate an unofficial
governmental agency of assassins.

From the famous assassins of the ancient and medieval Middle East to
the not-so-distant past in Qing's homeland, during the Cold War, there
were blatant power struggles between officially recognized state
assassin groups. And it was rumored that such struggles might still be
ongoing, though whether it was just a conspiracy theory or not was
another matter.

So, to think that there were even private assassin groups.

Moreover, these groups were so well-known that they were even
included in the ranking games of the ancient, primitive, and uncivilized
Zhongyuan, such as the Four Great Assassins or the Five Great
Assassins.

Qing thought, 'How in the world do they handle the grudges?'

It was unimaginable that among the targets of assassinations, there
wouldn't be someone connected to an incredibly powerful and
absolute master.

In a world where it was said that you could meet all the children of the
world by connecting through just six acquaintances, a scientific
principle to boot, she wondered if they didn't risk utter annihilation if
they crossed the wrong person.

Then how could famous assassin groups still exist and operate?

If a person involved in this matter were to hear Qing's question, they
might answer as follows.

They don't exist for long.

How do they handle grudges?

They can't.

Is there a way to avoid touching the acquaintances of absolute
masters?

If there was such a method, please let us know. If someone touches
the wrong person, it's a chain of massacres, a complete and utter
bloodbath.

The nature of human connections is unpredictable, so even those with
noble status and lowly servants can form bonds of loyalty. As such,
recklessly killing for money will eventually bring about retribution.

Countless assassination groups had disappeared throughout history,
and this was precisely the situation that the current assassin's guild,
the Assassin's Edge was facing.

The Heavenly Demon Divine Cult's secret operatives were former
assassins, and their elites could not show themselves before Qing.

This was because they had not lived sufficiently virtuous lives.

According to the Divine Cult's doctrine, they followed Angra Mainyu,
the embodiment of evil, during the era of the Heavenly Demon,
representing destruction and hatred.

However, now that the new master had descended, they were to follow
Ahura Mazda, the Heavenly Demon who was also the embodiment of
Heaven, radiant light, fire, and the sun itself, to conquer the world with
newfound goodness.

For reference, the Heavenly Demon Divine Cult's doctrine warriors had
spent their entire lives dedicated to such skillful rationalizations.

Thus, due to the sins of following the laws of the old era, they were
undergoing the harsh punishment of not being able to serve their
master directly, only able to admire him from afar.

As a side note, these true believers were making every effort to live
virtuously.

Today, I saw trash on the street, so I cleaned it up.

Who am I? A follower of the Heavenly Demon Supreme.

Now, instead of spitting on old folks struggling on the street, I go and
help them up. If there are vulnerable people being bullied, I intervene,
listen to the circumstances, and mediate. I help orphans, widows,
lonely elderly, and the disabled, and I try to prevent violence in the
streets and maintain order. Etc…

Therefore, the employees of the Seolga Merchant Guild, whom Qing
considered to be defectors from the Heavenly Demon's northern
outpost in the far north, were involved in gentler operations like
espionage or information gathering rather than assassination.

And now, the perfect opportunity for these true believers to
demonstrate their skills had arrived.

The incarnate god and revered Heavenly Demon Supreme, who had
descended to the mortal world, had commanded them to get rid of
those assassin scumbags!

Originally, assassins were best understood by other assassins.

Moreover, they had obtained the lower-level codes and even the
structure of the lower ranks of the Assassin's Edge.

Thus, a certain Mr. Geum, who had been scooping rice at a grain
merchant, was suddenly dragged away, and a certain Mr. Wang, who
was building a house, was surrounded by shoulders and taken away.
Some shops were raided by strangers who opened underground doors
that not even the owners knew existed, and descended en masse.

As a result, the assassins of the Assassin's Edge were imprisoned in the
basement (a terrible place where the sun couldn't reach), and the
miscellaneous assassins, who were deemed mere trash polluting the
mortal world, were sentenced to death by the Heavenly Demon
Supreme.

Meanwhile, Qing was reaping the benefits, with Righteous Karma
steadily increasing as she was recognized as the ultimate authority.

It was also a moderate benefit for the people of Xi'an, who unknowingly
saw the city's trash disappear, and it was a net positive for the world at
large.

"As of this moment, we are closing down this branch. Take only the
top-grade ledgers and lists, and burn the rest. Damn it, who crossed
whom on which side?"

The head of the Assassin's Edge's Xi'an branch, Heuksal, gritted his
teeth.

The history of the Assassin's Edge was a history of annihilation.

When they were wiped out, other assassins would simply swallow up
the name, thus continuing the legacy.

So, to be precise, the current Assassin's Edge, led by the Heavenly
Slaughter, was in its second generation, with a history of just over
thirty years.

However, even though the history was not long, the assassin group's
efforts to avoid total destruction had been long and continuous.

Vertical, compartmentalized organization, codebooks divided into
upper and lower levels, strict separation of top-grade and regular
commissions, and so on…….

In addition, when recruiting new members, they chose those who
seemed to hate the world and managed loyalty through thorough
indoctrination of loyalty.

But still, things happen.

Just a few years ago, they lost dozens of valuable assassins in Hubei
and were just starting to breathe again when another disaster struck.

He knew right away which one of them had betrayed him.

But he didn't know why it had happened.

Still, if there was a silver lining…

It was that the betrayal came from someone around the middle of the
vertical hierarchy, specifically around the solar plexus, so the upper
echelons, the most valuable assets of the Assassin's Edge, were not
exposed.

However, with this incident, along with the Hubei disaster…

With both limbs lost and only the head remaining, it seemed that the
current Heavenly Slaughter, the big brother, would have to dedicate
himself solely to the recovery of the Assassin's Edge and pass on the
legacy to the next generation.

At any rate, the situation was clear.

The Assassin's Edge would have to close shop for at least the next ten
years and focus on raising new limbs.

The head of the escort agency, the former top doctrinal warrior, Chief
Escort Cho, knelt down.

Then, with a determined expression, he took out a long dagger and
held it in reverse.

It was the perfect posture to stab himself in the abdomen.

"I have no excuse. I will atone with my life, this worthless life."

"No, put that knife away. But you have good skills. Where did you
suddenly pull out such a long dagger from?"

"How can you be so benevolent, so merciful? It is a dazzling,
magnanimous mercy that is blinding……"

"Stop that and, um. So you couldn't find them in the end?"

"Yes. We captured twenty-eight of the Assassin's Edge, but they were
just small fries who knew nothing about the higher-ups, the core
members, so, ahem."

Chodaeam eventually shed a tear.

Qing asked, bewildered.

"Why are you crying?"

"I am ashamed of myself. To think that I couldn't even root out such
lowly assassins and showed such a pathetic appearance to you,
Miss…"

Chodaeam continued to mutter to himself afterward.

Those Assassin's Edge bastards, no, those assassin bastards. I will never
forgive them. From now on, they will not be able to live under the same
sky as me…….

It was a mutter filled with a terrifyingly vivid hatred.

Well, was failing to find the assassins of the lumberjacks such a face-losing
event that it would make him harbor such intense hatred?

Well, the people of Zhongyuan are a bit like that.

They do seem to consider face and life to be of equal weight.

Qing understood and moved on.

It could be said that the loss of nearly thirty points of Evil Karma was a
virtuous and beneficial hatred for the world.

"I am truly sorry for not being able to help with your great endeavor. I
cannot express this feeling in words, and I dare say that my guts are
wrenching in agony."

"Hey, don't be like that. Thanks to you, I had fun too."

Qing's eyes sparkled, clear and bright.

Thanks to the old man and his minions, Qing had raided underground
hideouts two or three times a day, and although she missed the
witnesses of the Jangheung Trading Company disaster she was
targeting, she had cleared out plenty of trash.

"But the great endeavor you aimed for, to expose the wrongdoings of
that wicked and nefarious woman of the Jangheung Trading Company
to the world, has been hindered by these inadequate ones. Ahem, I
should indeed atone with my life-"

As Chodaeam took out a long dagger again from somewhere, Qing
quickly cut him off.

"It's fine. What do you mean hindered?"

"Ah. Indeed! As expected! It is a radiant wisdom, yes, such a radiant
wisdom! How could this insignificant one dare to fathom Miss's
boundless capabilities!"

"What the hell? Does flattery get you something?"

Why is this uncle so dramatic?

Anyway. Whatever.

"Who needs secrets in this world? What is it again, four somethings?"

Cheonjijijiyeojiaji, the heavens know, the earth knows, you know, and I
know. Since four know, it is called the Four Knows.

It was a saying from the Later Han Dynasty when a official named
Yang Jin refused a bribe.

To refuse a bribe during the chaotic Later Han period, this official
named Yang Jin was a decent person, but as a person of the Central
Plains, he was a failure, a non-Zhongyuan person, or even an
outsider.

At any rate, the Four Knows meant that there were no secrets in this
world.

"To put it simply, more than three thousand people died because the
dike collapsed. Why did it collapse? Because a young lady from the
Jangheung Trading Company embezzled materials. How are we going
to deal with this young lady? Since the lumberjacks who could testify
have already been assassinated, we need to find the assassins to testify
instead. That's it, right?"

"Yes. I am listening to your esteemed opinion."

"Since everyone already knows who did it, why not just let a few
assassins live and have them testify that they were commissioned by
the Jangheung Trading Company to kill all the lumberjacks?"

"Wouldn't that be false testimony?"

"Hey, everyone already knows that the assassination was done by the
Assassin's Edge. What's the point of needing the actual person when
the sky knows and the earth knows? I mean, let's just use some actors
to play the lumberjacks. Since everyone already knows that the young
lady from the Jangheung Trading Company did it, what's the point of
needing real witnesses?"

In other words, she was suggesting fabricating the witnesses.

At that outrageous suggestion, Chodaeam couldn't help but shout
aloud.

"Oh! Indeed! That is the will of the heavens!"

Thus, in the center of Chang'an, on Chang'an Street (长安街), people
with bizarre appearances stood.

For reference, Chang'an Street also exists in Beijing.

Since Chang'an was used as a byword for the most prosperous place in
the world, the street that ran across the front of the main gate of the
Imperial Palace in Beijing was also named Chang'an Street.

And since the main gate of the Imperial Palace in Beijing was called
Tiananmen, which contains the grace of the Son of Heaven to pacify all
under heaven, a place where nothing happened in the past in Qing's
hometown was none other than Beijing's Chang'an Street.

Anyway, aside from Beijing, Xi'an''s Chang'an Street was a bit
outdated, but it was once called the center of the world, so it was
packed with people, half air and half heads.

In the middle of it, a platform was erected, and people with bizarre
appearances revealed themselves.

Some had missing fingers, while others had their forearms wrapped in
cloth, leaving the lower part empty.

Of course, when something to see appeared, people gathered. But this
time, the unofficial greatest beauty under the heavens, the Heavenly
Flower Sword, was among them.

Of course, even those who did not know the Heavenly Flower Sword
could see that she was a beauty that made it seem as if another sun
had appeared on the ground under the heavens. So, whether it was
unofficial or not, anyone with eyes would naturally be drawn to her.

As a result, soon all the heads in the street gathered, making the ratio
of air to people two to eight, to the point where breathing felt
suffocating due to the smell of people.

Then, Qing took a deep breath.

One. First, make the audience your allies.

"Everyone, isn't this the very center of the world, the very center of
Zhongyuan, the most central Chang'an Street in Chang'an?!"

"That's right!"

"Yes! The very center of Zhongyuan!"

Qing's glib tongue, which the Grand Elder of the Tang Clan described as
the very embodiment of hell's beak, a formless poison in and of itself,
began to loosen up.

As the center of the world gradually shifted eastward, first to Luoyang
in the previous era, and now even further east to Beijing, praising
Chang'an as the center of the world immediately won the favor of the
people of Chang'an.

Qing then listed the things that would please the people of Chang'an.

Since those who had been part of the Heavenly Demon Divine Cult's
secret operatives had done their research on what the people of
Chang'an would like, the words that came out of Qing's mouth were
things they would enjoy.

Thus, the pride turned into heat, and as August's hot weather simmered,
Qing brought up the main point.

"And so, to all the warriors gathered here in the center of the world,
this girl, the Heavenly Flower Sword, Ximen Qing, wishes to denounce
an outrageous, utterly filthy, and appalling crime!"