\chapter{Fire In Chang'an (12)}

"Ugh! Ugh!"

"He's gagged, you see?"

"This profane thing kept trying to bite his tongue off, you see."

"Hmm. One doesn't die from biting off their tongue, though."

"Young Lady. When these ones bite their tongues, it's a trick to say they won't speak."

"Wow. What a man of honor. He's willing to do that for loyalty? I admire the courage, but his guts are too big for his brains. If it were me, I wouldn't be able to stand that shit. I'd keep him alive until he regrets it so he can never die."

"Ooh. Indeed! Excellent! If we display him somewhere like that, wouldn't it serve as a good example?"

"Hmph. Well. You heard him, right? If you bite your tongue off like an idiot, I'll cut off your arms and legs and raise you like a beast. Also, I don't know why you're trying to be loyal when it's not even for a good cause."

As Qing spoke, she removed the gag.

"Ptooey!"

The assassin attempted to attack as soon as he was ungagged.

Unfortunately, Qing easily blocked it with the gag in her hand.

"You bastard! How dare you!"

The escort agency's man was enraged.

It was hard to tell whether or not he was overreacting, but wasn't she blocking it anyway?

"Ooh. A terrifying attack. Is that a poison needle that melts flesh and bone on contact and makes your nose fall off from the stench?"

"Kill me. I have nothing to say."

"Why? You can do something good before you die. It'll help you clean up all those harmful pieces of trash, just a tiny little bit, you know?"

"……"

"You're going to keep your mouth shut, huh? Well. This is getting interesting. How can I make this piece of trash talk? Oh."

Qing spoke to herself and suddenly realized something.

I was talking to myself about the answer.

"Mister Escort Agency. Can I start a fire here?"

Then, the escort agency's man suddenly knelt down.

"I apologize! The ventilation is not good, so the best we can do is light a charcoal fire. I have failed to understand the noble intentions of the Young Lady and dared to bring you to such a humble place. I apologize! For such irreverence! I shall apologize with my arm!"

And then he took out a long dagger from his bosom, truly looking like he was about to cut off his own arm.

Of course, Qing thought it was all a show, knowing he would be stopped anyway. But this guy had a talent for making people feel sorry for him with his great acting.

"No, what are you doing? Why are you apologizing when I'm the one being picky when you're letting me use this place?"

"Sniff, you are so merciful……"

However, the escort agency's man felt like his heart was sinking.

The symbol of the Heavenly Demon Divine Cult was the divine flame, the Sacred Fire.

The Sacred Fire of the Divine Cult burned brightly with light, yet beneath the divine flame was a pitch-black darkness, an impenetrable abyss.

It could be said that this was the Heavenly Demon Supreme himself, who governed both good and evil, light and darkness.

Therefore, since the Living God was on this earth, it was only natural that she would use the holy fire to punish sinners.

How could he have not realized such an obvious, natural principle, as plain as the rising and setting of the sun and the moon? It made him want to die of shame.

Thus, the foolish one, not knowing the brilliance of the light, wished to atone by cutting off his arm for his ignorance. For it was made of bone, flesh, and blood, weighing seven geun1, and as he did so, the Heavenly Demon Supreme laughed and said, 'Everything was borrowed from you when I arrived on this earth. Therefore, do not trouble yourself with your foolishness. For I am already satisfied……'

The escort agency's man, a high-ranking evangelist of the main temple of the Heavenly Demon Divine Cult, was filled with infinite emotion, writing the scriptures that would be passed down to future generations in his heart.

"Crazy bastards……"

The assassin, who was still alive, muttered while watching the whole scene.

He still hadn't given up.

Wow. This one is going to be tough.

Qing swallowed dryly, feeling a sense of tension as if she had finally met a worthy opponent.

"Well. From now on, we'll slowly roast you from your limbs, burning you to a crisp. Hmm. If you tell me everything you know along the way, you can die a very comfortable death."

"Crazy bitch. Who would reveal information after hearing that?"

"Instead, if you hold out until your shoulders and the ends of your legs are completely turned to charcoal, I'll acknowledge that you won and let you live. I'll let you live forever. I'll let you live the rest of your life eating pig slop until you die of old age. Since people get bored just eating and sleeping, I'll even let you fuck pigs. But if you beg me to kill you, there's no going back on your word, you know?"

It was a horrifying thing to say.

In the past, was this what it felt like when the Empress Dowager, who reached the heavens with her wickedness, spoke? Like she had erased the single most used character in Chinese from the face of this earth?

Originally, in ancient times, the most widely used character for pigs was the character '彘'.

However, after Consort Qi, the wife of Liu Bang, introduced the utterly heinous punishment known as the human pig, people found it so horrible that they avoided using the character altogether.

But the Empress Dowager might feel wronged.

After all, she had gone through all sorts of hardships as that bastard Liu Bang's wife. When he was running around, she had served a prison sentence for several years, taking the fall for her husband's crimes.

At that time, a prison sentence was a horrific experience akin to being a plaything for bored jailers, yet she had obediently taken her husband's punishment.

Despite this, Empress Dowager had remained faithful and followed only her husband. However, as soon as Liu Bang became Emperor, he neglected her, calling her a dirty and evil woman. Of course, anyone would have snapped and gone mad.

In the first place, that scumbag Liu Bang was treachery itself.

He swore brotherhood with Xiang Yu, calling him Big Brother this and Big Brother that. Then, he sucked up to him to receive all kinds of benefits before stabbing him in the back. It was truly a disgusting display of character. It was no wonder his descendants would go on to destroy the nation, leading to the emergence of the first peasant rebellion, the Greenwoodsmen, followed by their juniors, the Yellow Turbans, and then traitors like Dong Zhuo and the Cao family.

It was even to an extent where a mere peddler, who was nothing but a beggar claiming to be a part of the Liu family, could talk about taking over the entire world.

It was quite funny. In the West as well, there was a similar story of a beggar who shined shoes going on to talk about stocks, leading to the Great Depression, a festival of mutual suicide.

In the East, a mere beggar who sold straw sandals was talking about taking over the world, so naturally, it was an era where millions died.

Fortunately, the lineage of this detestable Liu family was cut off by the Sima family.

Moreover, they gave up the world after taking it, dividing it into sixteen parts. This was why the Sima family was considered the greatest hero in the history of Zhongyuan.

"Y-You…! You're a horrible bitch! What kind of person says such things! Just kill me! Kill me!"

"I don't know. What kind of person kills people for a living? Anyway, I don't see why you're talking like this will ever happen to you. Do you think you'll ever get caught and die a miserable death? Or did you think a parasite who lives by selling the lives of others would be respected and live a long and happy life? If you lived like trash, shouldn't you go like trash? Isn't that how a proper world should be?"

The Lord of the world said, 'At the end of evil deeds, only a miserable end must exist. This is the right image of the world that you must cultivate……'

The eyes of the escort agency's man, the high-ranking evangelist, sparkled as he listened in.

"Kekeke, fine. I won't deny that I lived like trash. Then what about you? What gives you the right to do this? Isn't killing people the same for both of us?"

"Ehh. Humans? The only humans here are me and, hmm. Mr. Escort Agency should do a bit more good deeds. You're a bit on the edge. A bit dangerous."

"I will make an effort!"

Qing erased the expression from her face as she looked at the assassin.

"We're not having a conversation right now. I want to know who the bastards who hired the Jangheung Company are and where I can find them. It's only those words I want to hear from you. So let's have a little competition to see who wins through torture."

"Crazy bitch. You're completely insane."

"Is being called a mad bitch better than being called a horny bitch? Well then, be careful not to bite your tongue off. If you become mute, I'll have no choice but to burn all your limbs and keep you like a pig, serving you like an honored guest."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Why do you think they do that? I don't get it."

"What are you talking about?"

The escort agency's man, Cho Daeam, answered the question.

"If you're going to talk, it's better to do it nicely from the start. Why do they make people go through all this trouble before they start crying and spilling the beans? Ah, my clothes are all smelly from the burning."

The assassin had made a resolution.

He had decided to betray the grace of the hitman agency that had found him as a child and raised him into a proper assassin, choosing to repay such kindness with death.

However, as his fingertips began to sizzle over the charcoal fire, he quickly realized something.

Wow. This hurts way more than I thought it would. It's driving me insane. I don't think I can handle this. No, never. Even Buddha can't stand this. No, I swear on the Heavenly Slaughter Star. This is not the assassin's way.

The assassin had gained a great realization.

So the assassin cried.

He cried because it hurt so much, he cried because he felt sorry for himself for suffering like this after trying to hold out, and he cried because he was ashamed of himself for betraying the hitman agency that he had wanted to protect with his life.

However, Qing was not a fool when it came to tormenting others.

She knew that the credibility of information obtained through torture was poor. As such, she knew she had to go through a thorough verification process to determine if the information was truly reliable.

Because when people are in pain, they tend to say anything to escape it. Furthermore, they were prone to hating and resenting the one who caused them pain, thus mixing in lies to fuck them over.

So she had no choice but to roast him more thoroughly.

She roasted, asked, roasted, asked, roasted, asked, and roasted and asked again.

Because the attitude of the guy before being roasted was so wicked, she had no choice but to go through several rounds of verification.

This was why one should always be careful with their words.

If he had been polite and humble from the moment he was caught, showing respect, he wouldn't have suffered this much.

However, the effort put in did not yield much in return.

"He should have just said he didn't know. Why did he act like he knew everything? In the end, he just said that I should follow the highest-ranking guest line to find out."

"Young Lady. Then, shall we leave the rest to us?"

What Qing didn't obtain wasn't much, but the information obtained by Cho Daeam was enormous.

It was information about the internal workings of the hitman agency, straight from the mouth of someone who was roughly in the middle of their hierarchy. It included a partial organizational chart, lower-level codebooks, insignias, methods of contact, as well as the personal information of mid-level managers and how to summon and contact them…….

"Eh? The Ilweol Escort Agency? Why?"

"Hehe, well. That is. Uh, um, um. That is, gold and silver. If we raid the assassins, gold and silver will pour out, right? Running an escort agency requires a lot of gold and silver. Moreover, I was deeply moved by the Young Lady's intention to eradicate those trash-like assassins. Since he mentioned such information, we also have our own methods to find out."

"Hmm. No matter how much you like gold and silver, wouldn't that be dangerous? They're the type to draw their swords as soon as they think you're looking down on them."

"If Elder Choi helps us, it wouldn't be that dangerous. Thank you so much for your concern. It is truly a boundless, great, and merciful act of love."

"Hmm. If Gramps is there, well."

Gramps was an Unrestrained Realm Master and the staff members of the Seol Clan, who were presumed to be deserters from the Heavenly Demon Divine Cult, were all martial artists who were at least First-Rate.

With that level of skill, it might be possible.

"Then I'll leave it to you. But if it seems dangerous, back off immediately. Okay?"

"Sniff, yes! I understand! This unworthy one will defend it with my life, my very life!"

At that, Qing tilted her head.

"……? Did you understand what I just said?"