\chapter{Fire In Chang'an (14)}

The crowd in Chang'an gulped.

After all, she had said it was a heinous crime, one too dirty to even be uttered.

Just who had committed such a great sin that she took so long to get to the point?

"Have you all heard the news of the great flood in the land of Naknyeong? Last night, a great flood suddenly struck, so much so that the city gates were smashed. Because of that, over 2,000 people died in Naknyeong, and more than 1,000 are missing, with their bodies yet to be found. In total, more than 3,000 lives were lost in a single night."

Since it was not within their own region, the people of the Shaanxi Province merely expressed their sorrow at the disaster that had occurred in the Henan Province, thinking that they should check their own levees once more.

However, the news of 3,000 people dying was quite shocking, as floods in Zhongyuan were not just a disaster for others, but could happen to anyone.

"The reason for this great damage was that a newly built river levee from that year's winter had burst. If the waters had been allowed to flow naturally, the city might have just been submerged a little. But because they blocked the water's path, it all came rushing down at once. However, this levee was originally a grace from the Emperor that should not have burst. But because it did, more than 3,000 lives were lost."

Qing's last words caused a sudden hush to fall over the surroundings, so much so that one could hear the sound of everyone's blood draining from their faces.

It was because she was saying that the disaster occurred because the levee was built unnecessarily, that it was the fault of the Emperor, who ordered the construction, for causing such a disaster.

It was truly the words of a traitor.

This was not something they should keep listening to.

As people were looking for a way to escape…

Qing skillfully shifted the blame.

"Of course, His Imperial Majesty, in his benevolence, ordered the construction solely for the welfare of the people. His grace is unforgettable, etched into our bones. And should we not all shout 'Long live the Emperor' and give our thanks for His Majesty's watchful care?"

Phew. So it wasn't about being a traitor, huh.

A collective sigh of relief was heard, sounding like a typhoon sweeping through the surroundings.

"But the levee burst. More than 3,000 people lost their lives, even more lost their families, and even more lost their livelihoods. But there was a reason why the levee, granted by the Emperor, had burst. And that is because…"

Qing paused here and looked around, making eye contact with the crowd.

They responded with gulps, showing they were listening closely.

Qing, after building up tension, finally uttered these words.

"Because they deliberately built the levee to collapse, to burst from the start! The materials that should have been used were not even half, I repeat, NOT EVEN HALF of what was needed! As such, it could not withstand the torrential rain! For 3,000 lives, just to line their own pockets with silver and gold! To make money! There are those who deliberately built it to collapse!"

"Gasp."

"Who would intentionally burst the levee!?"

"Who in the world would commit such a heinous act!"

"They burst the levee to make money!"

There were some who were particularly loud in their indignation.

Qing was unaware, but these were the Heavenly demon Sect's plants who voluntarily stepped up because no one had ordered them to, just to hear more of what their esteemed Heavenly Demon Supreme had to say.

"So, who is it!? Who is it!"

"The flood control construction in Nakha was handled by the Jangheung Corporation, which you are all very familiar with."

At this, the crowd gasped in shock again.

The Jangheung Corporation was the largest corporation in Shaanxi, literally meaning that they were the best. Additionally, the name 'Jangheung' was a prayer for Chang'an's prosperity.

In other words, it was one of the prides of the people of Chang'an.

"N-No way!"

"Do you have proof?! Do you have any evidence!?"

The voices of the people grew louder.

Qing waited for them to speak their fill, before finally opening her pretty lips once the attention was gathered again.

"The people here are the proof. Is there anyone from the Chuga Lumber Mill? This is the Head Carpenter of Chuga Lumber Mill, Yeom Hansu."

At that, one of the people standing on the platform stepped forward to Qing's side.

However, he was beaten so badly that his face was swollen to twice its size, making him completely unrecognizable.

Of course, the real Yeom Hansu was killed by an assassin's blade. Unfortunately, his family also died with him, but it was uncertain if they could reunite in the afterlife, as there might have been a difference in their Evil Karma.

At any rate, thanks to this, there was no one who could sensitively determine whether or not the person standing there was a fake, allowing a mere assassin from the Killing Star to impersonate him.

"I am Yeom Hansu, the Head Carpenter of the Chuga Lumber Mill! Under the orders of the Jangheung Corporation, I reduced the materials used in the design by half! I replaced strong soil with sand and mixed gravel into the cement! This was to replace the materials that should have been used with much cheaper ones!"

At this, the crowd buzzed loudly again.

The Chuga Lumber Mill was well-known even in Seoan, and even then, since there were only three or four Head Carpenters, there were more than a few who had heard of Yeom Hansu.

It was a public denouncement made in broad daylight.

No one could think that someone would bring a fake to commit fraud, which was the blind spot.

Even though his face was swollen and unrecognizable, they just thought he had been beaten for doing something wrong. After all, there was no doubt he was a complete bastard.

It was then.

A sharp outcry cut through the crowd.

"That's not true! That man is not Yeom Hansu! He's a fake!"

Another commotion arose.

Hmm. As I thought, there's one who recognizes him.

Qing inhaled deeply.

"Who was that just now? Which one of you said that Head Carpenter Yeom was a fake? Do not hide, but come here and speak boldly."

"It was him!"

"This person said it!"

Due to the primitive entertainment culture of ancient China, the people of Zhongyuan would not miss such an exciting confrontation.

The one who had shouted was immediately pushed out and shoved to the front of the crowd.

He had a flustered look on his face, but soon he cleared his throat and took a deep breath.

And just as he was about to say something-

Smack!

Qing's foot, flying just above the ground, struck the man's calf sideways.

Crack. The clean sound of bone breaking traveled up her instep, making Qing try hard not to smile.

After all, it would be somewhat inappropriate for an accuser to smile in such a public setting.

Qing grabbed the collapsing man by the scruff of his neck and pulled his arms wide open! With such violent strength, it was inevitable for his clothes to just rip apart.

In an instant, Qing turned the man into a shirtless individual and jumped back onto the platform.

"Everyone! Do you see this tattoo here! These two letters spelling out 'Yisim' are letters tattooed on the bodies of assassins, cannibals who make a living by killing people!"

Wasn't it obvious that no one could recognize the state of the man whose face was swollen to twice its size, making it impossible to tell if it was the real Yeom Hansu or not?

But there was someone who claimed it wasn't him? That he was a fake?

Unless he was the one who killed the real Yeom Hansu, who had suddenly disappeared after getting drunk, or someone related to him, how could he have known whether Yeom Hansu was dead or a fake?

I thought that no one could be so foolish as to get caught so obviously, but here we are.

"Everyone! Do you know that there were a series of funerals at Head Carpenter Yeom's house recently?! It's because the Jangheung Corporation sent assassins to the Head Carpenters involved in the construction to hide their crimes! If any of you work as carpenters, you'll know that many renowned Head Carpenters have either died or disappeared recently!"

At this, there was another commotion.

There were indeed some who actually worked as carpenters among them, so they raised their voices in excitement upon hearing a familiar story.

That's right! That's right! Carpenter Wang and Carpenter Gang, both from the Jang Carpenter family, had funerals! I heard that the Cho Wang Mill might have to close shop because both of their Head Carpenters are gone!

Of course, the proportion of carpenters was quite high, as the faithful believers, possessed by the spirit of carpentry, were actively stirring up the atmosphere.

"All these guys with their shirts off are cannibalistic demons from the Killing Star! They all have the tattoo 'Yisim' under their left chest. This is the proof!"

One might ask why anyone would be foolish enough to tattoo themselves as assassins, but in reality, criminal organizations like these often used tattoos to clearly mark their affiliation.

In the primitive, ancient, and uncivilized Zhongyuan, there was only one type of person who got tattoos.

Criminals.

Tattoos were used as a visible mark for everyone to see, indicating that the person was an identified criminal.

Criminals who had not yet been caught used tattoos to prevent betrayal and foster a sense of belonging.

If someone betrayed and left, all they had to do was spread rumors in that area.

They just needed to say something like, 'Someone in this area is actually a former criminal. You can tell by the tattoo on this part of their body.'

So once tattooed, one could not escape the criminal organization.

This was why criminal groups like these would first decide on a name and then a tattoo when they were formed.

This was also why tattoos were looked down upon and disdained, regardless of whether it was the East or the West.

Tattoos were used for shamanistic purposes by the uncivilized ancient people, but after humans established societies, tattoos were essentially nothing more than marks of disgrace.

"I am Cho Junam, an assassin from the Killing Star. I lived disguised as a rice seller in Ogamigok, and in reality, I am a Human-Ranked assassin from the Killing Star. Until now, I have received payment for over fifty commissions, urgh."

Qing struck the back of the assassin's head and urged him on.

"What do you mean commissions? Speak properly, will you?"

"I have killed over fifty people for money! This time, at the request of the Jangheung Corporation, I killed Head Carpenter Wang Jungsam, who was involved in the flood control project!"

Following him, assassins without fingers, and sometimes even without wrists, confessed their names, disguised identities, and the names of the dead Head Carpenters.

Qing kept her promise.

These were the ones who would live as a reward for their false testimony.

However, their right hands had been dealt with first, and it was uncertain how long those who had betrayed their own organization could survive.

But that wasn't something she needed to be responsible for.

If they want to live, they will. And if not, well, it's not my problem, is it?

At this point, the situation seemed clear.

The Jangheung Corporation had embezzled half the materials from the flood control project, resulting in a disaster with massive casualties.

Fearing that this crime would be discovered, the Jangheung Corporation sent assassins to the Head Carpenters.

And these were Head Carpenters who had worked with the Jangheung Corporation for a long time.

It was a truly heinous crime.

"Everyone, now I intend to go to the Jangheung Corporation and find out who planned this atrocious crime and how they will pay for their sins! I hope you will all bear witness to the consequences of this utterly wicked crime!"

Then Qing elegantly jumped down from the platform.

As she walked, the crowd parted, slowly making way for her.

The employees of the Seolga Merchant Guild, each holding a traitorous assassin from the Killing Star, followed behind her, looking like the proudest people in the world with their noses held high.

Naturally, the agents of the Heavenly Demon Divine Cult, who had been unable to stand before Qing and were just playing the role of a cheering squad, looked at them with envy.

And so, a procession followed Qing, with the agents of the Secret Investigation Unit behind her, and behind them, the entire crowd of Chang'an filled the broad street, marching together.

Qing, standing at the forefront, looked at Seol Iri beside her and sighed.

Then, looking at the old man on the other side, she quietly asked.

"Gramps, by the way, is this the right way to the Jangheung Corporation? Come to think of it, I don't know the way."