\chapter{Fire In Chang'an (15)}

Jangheung Corporation was the most prominent trading company in Shaanxi.

And the method by which a trading company flaunted its wealth was no different in the past, present, or future.

If they erected an imposing building on prime, expensive land and proudly displayed their signboard, anyone in the world would think, 'Wow, that's a really successful establishment'.

And where would the most prominent trading company in Xi'an choose to establish itself?

So, at the end, or rather the very beginning of Chang'an Street, a huge wall had been built, stretching endlessly. It was just a two-gak (thirty-minute) walk from where Qing had gathered people and made a fuss.

Thus, there were those who, upon hearing the plea, 'The Jangheung Corporation is bad, they're killers!', changed their expressions and quickly slipped away, immediately rushing back and huffing and puffing as they passed through the side door of the Jangheung Corporation.

Of course, the larger the scale of an organization, the stricter the hierarchy between ranks.

At the level of Jangheung Corporation, news could not reach the owner of the company directly in one go.

"Big trouble! Big trouble! Right now, in the market…."

In the market, people are crowding, a babble of voices, assassins are stabbing, carpenters are screaming, and the Jangheung Corporation, those bastards!

"What? Aigo, this is really big trouble. I can't stay here like this. I must inform them immediately……!"

And then, off they went again.

"There's big trouble! Right now, in the market…."

"What? What's that? No, first, report. Damn it, what in the world is going on?!"

And then, off they went again.

"There's big trouble! Right now, in the market……"

If Qing had heard the news being relayed from mouth to mouth, she would have ridiculed it as some sort of silly game of telephone played on TV shows.

However, there was a clear reporting structure, and no matter how urgent the situation, any misstep could create an issue that would come back as a disadvantage later, so naturally, one had to report to their superiors to follow the proper order.

After all, if one didn't, they would be the only one to suffer.

Thus, the Vice-Manager, who had heard the news through the grapevine, was finally able to climb the steps to the Lord's residence and meet the Lord of the Corporation.

"What's all the fuss about? Did one of the warehouses catch fire?"

Lord Nam Moon-seongsam, who was gently stroking a precious orchid, asked nonchalantly.

In fact, there were dozens of warehouses, so even if one of them caught fire, though it would be a pity, it was not something to make a fuss about. That was what Nam Moon-seongsam thought.

"Well, it's just that, right now, there are people gathered in the market."

"So what? Did they come rushing to attack or something?"

"Yes! That's……"

As the Vice-Manager urgently explained the situation, Nam Moon-seongsam, who was wiping the leaves of the orchid, accidentally tore off a leaf of his beloved plant.

"What!? The flood control project… No, immediately fetch Hae-ah, bring her to me first!"

Nam Moon-seongsam was now fifty-four years old, which was young if considered young and old if considered old, but on the outside, he looked almost like an eighty-year-old man.

When he inherited the family business, it was just a small trading company on the outskirts of the city, but now it had become the most prominent trading company in Shaanxi Province. The hardships he had endured in the thirty-five years since then had aged him prematurely.

The hardships endured in youth turned into ailments in old age, and despite all the good tonics and the care of a dedicated physician, these days, whenever it rained, his whole body ached so much that he couldn't stand, sit, or lie down without groaning.

So, he had gathered his children and told them that they should each show their achievements, and that only the best merchant among them would become the owner of the Jangheung Corporation, and then he was preparing to retire.

And the child who currently had the greatest achievement was his youngest daughter, Nam Moon-hae.

She had finally secured the flood control project and surpassed her brothers by far in the construction business. In fact, it wasn't just her brothers, but she had also broken the record for the highest amount earned by the Jangheung Corporation in a single project, with two carts filled with gold, excluding silver, entering the family estate.

Thus, as soon as he heard, he understood the situation.

Aigo, that child's ambition has gone too far and has finally caused a big accident.

Of course, even without being a seasoned merchant who had experienced all sorts of trials and tribulations, anyone in the world could have seen such an obvious story coming.

It was then.

-Summon the Lord of the Corporation! Summon!

-Summon!!! Summon!!!

-The Jangheung Corporation must explain! Explain!

-Explain!!! Explain!!!

The clear voice of a young woman and the loud chorus of the crowd that followed shook the very floor.

Even at this moment, there was news coming in, climbing up one step at a time through the frustrating reporting structure, stating that the crowd of Chang'an Street had gathered in front of the main gate.

It was such an urgent matter that one might have skipped a few steps in the hierarchy, but the fact that such a serious issue was still subject to rigid reporting procedures was arguably the fault of the corporation's owner, who had always emphasized and valued hierarchy and procedures.

After all, who would dare to skip steps in the procedure when it was likely they would be scolded for it, even if it was urgent? It was the way of the people of Zhongyuan to be terribly concerned about their own safety.

However, before the news could reach the ears of the Lord of the Corporation, time had run out.

No matter how grand the manor, if the walls were not fortifications and the gates not made for siege, they could not stop the steps of a peerless Master.

Fortunately, Qing did not have to march forward and then retreat in a disastrous manner.

It was purely out of luck.

Originally, although Chang'an Street's center was a crossroads, the roads extending up and down were significantly lacking in width and scale compared to those on the left and right. Therefore, there were two paths leading to the right answer from the beginning, meaning the probability was fifty-fifty.

Thus, after marching triumphantly with people trailing behind her all the way to the Jangheung Corporation, the news had already arrived and the main gates were firmly shut, with gatekeepers standing with spears drawn.

"Excuse me, I would like to see the Lord of your Corporation-"

"Go, go away."

What the hell? He's telling me to go away before I even finish speaking?

Qing ignored him and continued speaking.

"I do. Could you please open the gate?"

"That is not possible. Please leave. If you do not leave……"

The gatekeeper, who had been speaking tremblingly, suddenly trailed off. If they don't leave, then what? What will you do?

Qing's eyes, not missing a chance, sparkled.

"If I don't leave? What will you do?"

What are you gonna do, huh?

Are you gonna stab me with a spear in front of all these people?

"I, I will report this to the authorities."

"Through this crowd?"

"Uh. Um. Now that you mention it, that seems to be?"

The gatekeeper was at a loss for what to do.

"So, what are you going to do?"

"Aigo, good sir, could you please consider my position just once?"

"No. So, should we just resolve this like martial artists, with force? Now, you might get hurt, so please step back."

"W-Wait a moment……!"

What could a mere gatekeeper do in front of a Transcendent Realm Master?

Still, he had at least tried to stop her, which was commendable, so he might be able to save face later.

Starlight flashed and passed vertically through the very center of the main gate.

The iron bar, thicker than an adult's thigh, was holding the gate, but against Sword Force, unless it was a weapon held by a martial artist, metal was useless.

"Eek."

Seeing the long, drawn-out Sword Force up close, the gatekeeper stumbled backward in surprise. Qing took this as permission to pass and opened the gate wide.

Thus, she defeated the weak mooks!

As Qing walked through the wide-open gate with confident steps, the crowd, filled with righteous indignation, followed behind her.

However, they didn't know why their morale was so high, nor did they know why it should be so high.

Thus, as Qing took her place in the vast front yard of the Jangheung Corporation, as large as the grand manor itself, she did as she had learned from her life experiences.

"The Jangheung Corporation must explain the corruption in the flood control project!"

"Explain!!!"

Originally, when a certain number of people gathered, they tended to stop thinking.

Thus, the crowd filling the front yard of the Jangheung Corporation echoed Qing's last words, not really thinking about what this was or why they were doing it.

Anyway, as the commotion grew, people who were curious about what was going on came out through the wide-open gate, saw what was happening, and asked.

What's going on? Is there a feast?

It's not a feast, it's an execution. The truth is…….

What? Look at these outrageous bastards. Explain!!! Clarify!!!

Thus, finally, the heavy-bottomed Lord of the Corporation made his appearance in front of the Heavenly Flower Sword.

Qing looked at his physique and thought to herself.

Hmm. It seems this old man is also quite a son of a bitch.

Judging from the karma of Carpenter Jang, it seemed like he was just an old man who had lived like an utter bastard rather than just being involved in the flood control project.

In fact, in commerce, the idea that reputation contributed to sales, a very advanced technique based on reputation, was only established in modern times.

There was a prominent agitator and fabricator in the West, known as Grandfather B, who had made a great achievement in changing the breakfast culture of the Western people through agitation and fabrication, making them eat eggs and smoked pig.

There was even a famous Grandfather G who was inspired by Grandfather B and became his self-proclaimed disciple.

Anyway, it was only with the emergence of Grandfather B's marketing theories that reputation and image were first introduced, which was a completely new perspective, a pioneering of a new world.

It could even be considered a great achievement that changed the worldview of merchants.

Thus, in Qing's hometown, no one doubted the importance of reputation in marketing.

However, in the primitive and uncivilized ancient China, such a thing did not exist, so it was inevitable that a renowned merchant in the world would be a son of a bitch who took pleasure in exploiting others.

Of course, there was a merchant's virtue called the way of doing business, which emphasized symbiosis, generosity, and sharing.

And just like all these virtues, merchants were bastards who never practiced symbiosis, generosity, or sharing, which was why they kept being emphasized.

Therefore, upon seeing Nam Moon-seongsam's Evil Karma, Qing could immediately judge, Wow, this old bastard is a killer!

In fact, since it was the work of Miss Jangheung Corporation, she had been worrying about the extent of the punishment, but now she could clearly sort out her thoughts.

The death penalty.

"What is the meaning of this! Do you not fear the law of the nation! How dare you invade like a band of thieves and cause such a disturbance!"

Hmm. It seems everyone says something similar, huh?

To this, Qing responded.

"About that? Now. Look here. Sparkle, sparkle."

Qing raised her sword and manifested Sword Force.

It was a starlight that anyone could see was chillingly cold.

"Let's say a leader of a group of thieves, capable of using Sword Force, has invaded with her gang. What can the Lord of the Corporation do? Will you fight with your sword? Alright, if you're going to rush at me now, I'll give you a handicap of one hundred moves. You'll lose your head on the one hundred and first, though."

Faced with such blatant threats, Nam Moon-seongsam's words were choked off.

The words 'So what are you going to do?' were literal. If she started to lead the crowd in looting, the private soldiers of the corporation wouldn't be able to handle it.

However, Nam Moon-seongsam was a merchant who had built his own family, so he was different from the gatekeeper who had been flustered and pushed aside.

The weight of the wealth he had accumulated was different, and the experience shown on his face was layered so thickly that it was no longer the appearance of a human.

"Are you truly the leader of a band of thieves? Well, if you loot this corporation, do you think the law of the nation will leave you alone?!"

"Ah. The law. Right. Didn't you say you were on a first-name basis with the Provincial Governor of Shaanxi?"

"Hmph. It is just that I alone admire the Provincial Governor and consider him as such."

The Provincial Governor was the highest official of a province.

It was impossible for such a high official to openly say that he was on a first-name basis with a mere merchant, no matter how prominent a trading company it was in Shaanxi.

But he was indeed on a first-name basis.

That was how Nam Moon-seongsam answered.

To which Qing responded…

"Then, call the government troops."

"What? Fine, you seem to have something you believe in-"

"But, can you really call them?"

Qing grinned, showing a wicked smile.

"What if, by any chance, there is a criminal here who intentionally ruined the flood control project ordered by His Imperial Majesty by skimming off materials to make money? Wouldn't that Provincial Governor or any other official immediately arrest him and investigate his crimes?"