\chapter{Fire In Chang'an (11)}

Qing did not solely see the world through sight.

With the ability of her Awakened Divine Arts, she could read the flow of
the atmosphere with her skin, thus feeling a narrow area around her
body in all directions.

The movement of the assassins extending their daggers up and down
was caught by her senses.

Two daggers aimed at her neck. And two more daggers.

As if they were attached to each other's back, two more hands reached
out from between the assassins' armpits.

Thus, two more daggers rushed towards her lower abdomen and right
flank.

It was a splendid joint attack, as if an assassin with four arms was
extending four blades at the same time.

It was also a precise attack, targeting only the fatal points of the neck,
lower abdomen, and spleen.

In response, Qing had only two hands to counter.

However, two were enough.

Qing blocked the front of her neck with her left hand and at the same
time, clenched her abdominal muscles. Inhale!

Qing had already transcended the limits of a human with her physical
toughness. Moreover, the Protective Aura that she had developed
through a fight with the harsh cold had reached the realm of
effortlessness, enabling her to activate it automatically for defense.

If she just blocked her neck, which couldn't be protected by her
Protective Aura, then as for the rest… she could just let it come.

Finally, the sharp, blue tip of the daggers pricked her.

The well-honed tips of the daggers stopped, blocked by Qing's palm.
The two daggers aimed at her abdomen also failed to pierce her
abdominal muscles, stopping after only pricking her skin.

And Qing still had one hand left.

She pulled back her elbow, straightened her fingers, and then thrust
forward, piercing with a single, unstoppable strike.

One Principle Penetrates All.

Despite the grand name, it was just the third stance of the Three
Essence Sword.

The Three Essence Sword was, by Qing's standards, one of the lowest
tier of the third-rate martial arts. If she had to put it in a category, it
would be a Ninth-Rate martial art. As such, One Principle Penetrates All
was hardly capable of piercing through everything with one strike.

However, it could penetrate two people at the same time.

It pierced through well-trained abdominal muscles, penetrated the
soft and squishy visceral fats, passed through the intestines that
brushed her palm and back of the hand, and then pierced the back
muscles. Wow! Once more! Abdominal muscles again!

It was truly a one-for-two, buy-one-get-one-free, two-birds-with-one-stone, one-stone-two-kills, double-kill kind of joy.

The assassins were aggrieved.

Their daggers were blocked by a palm and failed to even pierce the
abdominal muscles, yet Qing, with just her bare hand, had pierced
through both of their stomachs.

If they were aggrieved, then they should have used Sword Force.

After all, if one was aggrieved, then they should become a Master.

It could also be said that they lacked the effort needed to reach the
Transcendent Realm.

"Haeuh."

Qing could not help but let out a sound of satisfaction at the joy of
double-kill.

But it wasn't over yet.

She extended her arm horizontally, lifting the two skewered men.

It was the monstrous strength that could pluck a mountain, lifting the
weight of two men with just one hand.

Usually, the upper body, including the head, was heavier than the lower
abdomen, so naturally, the skewered assassins' bodies tilted to one
side.

As such, in what seemed like a natural instinct, one of the assassins
firmly grabbed Qing's shoulder with both hands to support his flipping
body.

The one in front had something to grab, but the guy skewered from
behind had nothing to hold on to.

So what could he do? He suddenly hugged the one in front, causing the
weight of two people to lean heavily on one.

As a result, their bodies flipped, with two heads hanging below, and
the receptionist, who was just now getting up, could be seen between
the legs of the two men.

Qing bent her arm, drooping it like a claw. As such, the outer assassin
bumped his head on the floor, followed by the one in front.

The two men slid down, and Qing's grip held two strings of intestines,
stretching out from the stomachs of the men piled below.

Qing tied the intestines together into one.

Now that the two were connected by their intestines, they shared a
very intimate bond, making them the closest friends in the world,
physically.

Qing smiled in satisfaction and looked at the receptionist.

Now what will you do?

Will you be enraged, shouting that they're your comrades' enemies?

Or will you beg for your life?

Your Evil Karma says you're not someone I should spare, though.

However, the receptionist's response was none of the above.

He made a determined expression, then took something out of his
bosom and swallowed it.

"Now, let's have a nice conver, hey!"

Startled, Qing stomped on the ground, using the Heavenly Demon's
Teleportation Technique to dash forward at ultra-high speed and grab
the man's neck.

"Keuheuk, I'll be waiting for you in the netherworrrrldd!!"

It was a determined final word, complete with a sneer, but a hand
grabbed his chin and pulled, forcing him to scream instead.

It was because Qing was a wicked bitch who didn't care about other
people's final words.

After expertly dislocating his jaw, Qing shoved her long, beautiful, white
fingers deep, deep, deep into the receptionist's mouth.

"Ugh, eughk, oooegh, oooooegh, uub!"

The vile retching gradually intensified, until a tremor from deep within
signaled an imminent eruption. Qing quickly pulled out her hand and
threw the receptionist aside.

The pitiful receptionist rolled on the floor and vomited everything
inside him.

Qing frowned. Eww, gross.

Since there was a teacup on the table, she threw it towards his head,
thinking she should at least wash him off.

With a clatter, the glass shattered and tea spilled over him, making him
look a bit better.

"Why even try to commit suicide when you've done so much wrong?
Don't you have any sense of camaraderie? Look at all this. Even after
death, you're still being a nuisance."

"Keoheok, y-you. Do you know who you're messhing wi……"

"It's scary how you tried to commit suicide when you knew you were in
the wrong. Look, friend. You should live, even if it's hard and painful.
Grit your teeth and live. So, even though I'm going to make it so painful
that you'll wish you were dead, you shouldn't give up on your life.
Endure it with spite and malice."

"……?"

"Do you know what happens when you flip suicide?"

Qing asked as she approached the receptionist.

Then, grabbing him under his shoulder, she asked and answered by
herself.

"The answer is homicide."

"Argh!"

The process of removing the bones of his arm from his shoulder and
his leg bones from his pelvis was as natural as water flowing.

Even if the bones were dislocated, the muscles and tendons remained
attached, so it wasn't like he couldn't exert any force at all.

However, it hurt so much that one's mind usually went blank and they
couldn't see anything. When all four limbs were like this, one couldn't
even pass out from the pain, only able to scream with all their might
until their throat burst.

"Ah, damn. So noisy."

Qing ripped off the man's sleeve, roughly twisted it into a single line,
wrapped it around his dislocated jaw and the back of his neck, and
tightly tied it.

"Aup. Euhheup!"

If she had blocked his mouth completely, he might have suffocated.

The sound leaked a little, but it wasn't too loud.

Then she tried to grab his hair, but it was a mess from the earlier
process of telling him to spit out the poison, so she grabbed his ankle
instead.

What unspeakable agony it must be to have a dislocated leg grabbed.

Of course, Qing had no intention of understanding such agony.

"I told you to stop calling me that, didn't I? It's Gun Yeong. Gun. Yeong."

"Even if you call me that and that, the pronunciation is basically the
same. It's because of the, uh, whatchamacallit. The Connected Sound?
Whatever the rule is, it's something like that. Even so, in my heart, I
pronounced it properly as Gun Yeong."

Seol Riyi's eyes narrowed.

As such, Qing smiled and held out her left hand, which she had wiped on
her waist.

"Anyway, let's go back. Here, hand."

Seol Riyi obediently took her hand.

"But really, shouldn't I just call you that? It's really cute, though."

"I would prefer if you didn't."

"……Then what about Hole-ie?"

At that, Seol Riyi's forehead creased.

She tried to pull her hand away, but Qing held on tightly, causing her
hand to just flap around uselessly.

"Oh ho. What's this? What's with this tantrum? You don't need my hand
anymore? Fine. Let go then."

"No. No. No."

"Right. Good girl."

It was as if they were just returning after playing around, with one
dragging a body by the ankle.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Qing dragged the receptionist back to the surface, ah, although
climbing the stairs with his head bumping against each step was a bit
entertaining, Choi Leeong, who had been waiting, clicked his tongue.

"What is the meaning of this, wench? Are you a stray mutt? Tsk tsk."

"Ehh. I was trying to be gentle this time? This is neat enough."

Did I not splash blood around? I didn't even cut any major blood vessels
to wash my hair with blood like other times.

It was just that blood accidentally splattered on my face. It's not even
enough to drip down from my chin.

Choi Leeong wiped Qing's face with a pre-prepared, warm, damp towel.

The warmth and the careful touch brought a smile to her face without
her realizing it.

"Hehe."

"What's with the 'hehe', you mannerless brat."

"No, I mean, Gramps. It's not like I'm a child. Why would I need to be
mindful of my manners? Should I be all strict, stern, and serious,
laughing like, 'Heuheu'?"

"Hmm."

Choi Leeong's desire was for her to have more dignity and grace as the
leader of the Divine Cult.

But it wasn't like he could say that.

While they were talking, a certain gaze landed on them.

Not just a gaze.

The hand she was holding was squeezed a bit tighter.

"I'll ask this guy some questions later, so make sure he doesn't die.
And is there another wet towel?"

"I prepared more just in case."

Qing received a new wet towel and wiped Seol Riyi's face, who was
looking at her with a longing gaze, as if she was looking at a snack.

Honestly, Qing wasn't being rough because of any ill will or
annoyance.

It was just that she remembered how her mother used to scrub her
entire skin off during her distant past as a snot-nosed child. It was
excruciating torture. Now that she thought about it, she could
somewhat understand that feeling.

"It hurts."

Even though she said that, the corners of her eyes were slightly curved.
As an expert in raising Seol Riyi, Qing saw that she was showing a very
satisfied reaction.

But still, why does she not have hands or feet?

Why isn't she wiping it herself and just giving me the eye?

After returning, Qing ate a late-night snack. To be precise, she devoured
it like a pig, as if dinner was just an appetizer. Then, she headed to the
basement of the Sun and Moon Trading Company.

"Hmm. It might be a bit noisy."

"There is no need to worry, Young Lady. This place was designed with
perfect soundproofing that not even a scream of hundreds could be
heard by anyone in the world. Well, it's, um, a storage, a storage, yes, a
storage, haha, hahahaha."

"Oh."

Then Qing tilted her head.

"Why would a storage need soundproofing?"

"Uh, um. That is. Right. So, I also do not know. I-It was like this from the
beginning, so I'm also curious. Haha, haha!"

"Hmm."

It was like this from the beginning, huh? Was it used for something
impure?

Anyway, it was convenient for the moment.

When they went down to the basement, a man from the Sun and Moon
Trading Company, who said he was a Head Merchant, was fumbling
with the wall instead of an intact door.

Then, with a rumble, a well-camouflaged iron door was pushed open
with great effort.

Wow, the thickness of that iron door must be at least one chi.

Qing understood what 'perfect soundproofing' meant.

With just the thickness alone, it would be hard for an ordinary person to
open or close it, so how could any sound penetrate through and be
heard outside?

"Ooh. A secret storage."

"Now then. This way, Young Lady."

After lighting the lanterns inside, the Head Merchant, holding two
lanterns in each hand, walked backward to light the way, illuminating
Qing's feet with one lantern and Qing's feet with the other, thus
doubling the brightness.

Hmm. I get that my feet are bright, but what's the point if he's holding
two lanterns?

"Can I have one of those?"

"No! This is my joy in life! That is, it is a great joy for me to light the way
for the Young Lady. It has no other meaning, just that."

If that's what he says. Whatever.

Thus, after descending the brightly lit stairs and walking down a
considerably long corridor, another iron door appeared, and inside,
the captured receptionist was neatly tied to a rack, splayed out.