\chapter{Fire In Chang'an (7)}

Of course, I have to go in person.

In truth, the option of ordering someone else to do things was merely unfamiliar to Qing.

Even if she asked for something to be bought, she never asked for something to be done for her. In fact, she was always the one to do something for others.

She was the type of person who would make things worse by trying to do everything herself without considering the consequences, believing that everything would work out if she put her mind to it.

Thus, she set off into the night with Seolganom, both dressed in black.

It wasn't a stealth suit, just black clothing, and Seolganom's reasoning was as follows.

"By the time we reach Seoan, there will be quite a few people wandering around even at night. A stealth suit would be suspicious and other colors would stand out, so black clothing is the best option as it's both inconspicuous and does not seem strange to others."

In addition, Qing wore a veil and loose, slightly stiff clothing without a waist belt.

After all, Qing's face would shine brightly even at night, so it had to be covered.

"I look like a complete pig like this."

"Is there any other woman in Seoan who has two heads on her chest and two giant pumpkins the size of a door on her ass? Are you planning to announce your presence to the entire neighborhood by visiting so openly in the middle of the night? If so, just go as a sow then."

"Hmm."

"Sow. Bitch. Are there no other female animals that feel more obscene? It doesn't quite hit the mark."

"Stop saying things that won't work twice."

And there was one more person who had tagged along.

"Seol, you don't have to come along. Why don't you go and rest instead?"

"I will protect you."

"I'm being serious. I'd appreciate it if you'd just take my feelings into consideration……"

Her Inner Qi was poor, and her Outer Qi wasn't particularly outstanding either. Or was it? Maybe her resilience was a bit high?

Anyway, it was one incompetent fool with a pitiful cultivation technique, so who was she going to protect?

Still, her willingness to protect was admirable.

Actually, she's just like a pet.

What use are pets anyway?

If you have them, they make trouble, create more work, need to be fed, clothed, and walked if they're dogs. Cats need to be entertained, and so on.

If they get sick, it costs a fortune.

Despite all the uselessness of keeping dogs or cats, why do people still bring one, or even two, into their homes?

"Well, I guess something might happen. Let's go."

"Yes."

Then,she naturally held Qing's hand tightly.

Since Seol was prone to heat, she had been allowed to cool down with the chill of the White Hand Demonic Arts. Now, she held it as if it was rightfully hers.

However, from Qing's perspective, Seol's hand was hot and quickly became damp. Also, the kid has a lot of sweat on her hands.

It was a bit better at night, but it was still hot to hold hands.

Qing had achieved a resistance to heat and cold, roughly on the level of 'Slightly Resistant to Cold' and 'Slightly Resistant to Heat'.

But that meant she wouldn't be harmed by the cold and wouldn't suffer from heatstroke even in extreme heat.

When the temperature dropped, Qing still felt cold.

However, even when it was cold, her body temperature wouldn't drop and the heat would circulate evenly throughout her body, preventing frostbite and other cold injuries.

It meant she could survive naked in freezing sub-zero temperatures with strong, biting winds. As such, she had survived like that before. However, that didn't mean she didn't feel the cold.

Likewise, when it was hot, Qing was hot too.

It was just that she didn't have to worry about heat-related illnesses even in extreme heat, but she still felt just as hot.

However, even Qing now had a means to overcome this. She immediately invoked the useless chill of the Useless Cultivation Technique.

It was a useless chill that couldn't even freeze a block of ice, so it was just the right temperature to feel cool and refreshing.

Yeah, let's just say that I've already been repaid for taking in this pet.

After all, I don't have to worry about the heat for the rest of my life, right?

As soon as Qing thought of this, Seol, who was very sensitive to heat, clung to Qing's arm as if it were a lifeline.

Ah shit. It's hot, damp, and hard to walk……

Seriously, it's utterly useless.

At any rate, the two women and the quasi-woman, who had now clumped together into one entity, walked through the night of Seoan.

As they traversed the night streets, they eventually reached a street where quite a crowd was still wandering, even though it was late at night.

In truth, this was illegal in Zhongyuan.

By law, people were originally not allowed to wander around after the second hour of the night, which was past curfew.

Nevertheless, if a sizable crowd was gathered, the meaning was clear.

There were places where everyone pretended not to know the law, and the officials who enforced the law also pretended not to see. These were the red-light districts of large cities.

It wouldn't be strange to see three veiled women walking around there.

They continued down the fancy boulevard even at night, then turned into a narrow alleyway.

As they walked a bit further, the lewd moans of women echoed from all over the place.

The ancient, uncivilized technology of Zhongyuan was such that the windows of the brothels were left open, or rather removed, to deal with the heat of the night. As such, the embellished moans unique to prostitutes leaked out.

"Huh. Seol, are you sure you're going the right way? You keep talking about dicks, so did you just come here to get laid?"

"Hmm. I see what it feels like to be teased out of the blue. So this is why she never responds, no matter how much I tease. I don't like the sound of a perverted old man, so stop."

"Then are we here to find that technician to get laid? Woah, the dick still stands even while they're hiding for their lives?"

"I once heard that when a person's life is at stake, their sexual desire increases, but that's not it. These kinds of cheap brothels are originally the best places for fugitives to hide."

It was a structure with countless small rooms built in a long row, so it was easy to rent a room.

There were also the advantages of it being cheap and not requiring personal identification.

Plus, the authorities didn't conduct crackdowns.

At the same time, it had doors on both sides, leading to the outside and to the inner corridor, so it was easy to escape if necessary.

Even if that weren't the case, a few coins to a prostitute would be enough to pretend to be having sex and avoid the eyes of pursuers.

Since it was a den of pimps and thugs, men wouldn't be questioned even if they wandered around. On the other hand, if a woman was there, there was no better refuge in the world.

As Qing listened to this explanation, she thought.

As expected of Seol!

The greatest fugitive intellect!

Seoan was vast.

However, there were only a few streets that were permitted to operate at night (not really) and among them, this was the only cheap brothel area, so its size was enormous.

They listened to the feigned moans, although occasionally there were genuine ones mixed in. But nine out of ten were just fake moans mixed with nasal sounds to be heard.

At any rate, as she listened, something started to bubble up inside Qing, contaminating her eyes with a slightly more sinister color.

Hmm. Listening like this, it's kinda, a bit… arousing?

Come to think of it, why doesn't Seol react when she touches me?

It's understandable, though.

Honestly, it's not like having your breasts touched will suddenly make you feel all tingly and electric, like in the media of Qing's hometown.

Even when Tang Nanah touched her, Qing only felt ticklish, not pleasurable.

But, hmm. Listening to this, maybe?

I wonder what kind of sounds Seol makes.

I wonder what her cold, aloof expression will look like when it changes, when it melts.

But if it's just the sound and expression she makes when eating, well, that would be a bit disappointing.

I doubt it, though?

Hmm. Maybe some aphrodisiacs or something, if there are no side effects.

No, what am I saying? What's wrong with some side effects?

She's a useless, incompetent woman who can't do anything anyway. Shouldn't she be grateful to be used as a toy?

Who else would take in such a blunt and useless person? She's a moron who would have collapsed long ago if it weren't for me.

I should start by teaching her the Blissful Maiden Arts.

If I feed her some elixirs, even the Blissful Maiden Arts might improve in rank, right?

It was when Qing's eyes were gradually being tainted with evil.

"Now. Here we are. It's the fourth room."

"What? We're already here?"

As she was pondering how to play with Seol, they had already reached a very deep place.

Naturally, the deeper it was, the cheaper it became, so the dilapidated buildings, which seemed like they would collapse if knocked, were attached to each other.

"Wow. How did you find someone in a place like this?"

"I wonder too."

"Huh? Didn't Seol find him?"

"What ability do I have to find a person? I just told the elder that he was probably hiding in a place like this, and he found him by mobilizing people."

"Ehh, then what's the difference between that and Seol finding him? As expected of Seoan's greatest intellect."

"Why do you keep using that expression, the greatest intellect? It's embarrassing since when was I a smart person? Please stop saying such things."

Qing thought to herself.

So humble too.

It seems like I've met quite a few people who show off that they're smart, but the Demonic Cult's little kid doesn't seem like that at all. Jegalyi just has a lot of miscellaneous knowledge and likes to chatter.

Wang Big Tits, what was her name again? Bongchoon? I don't remember anything except that it was a countrified name. Anyway, she was just an outright weirdo.

Come to think of it, Seol is really something.

Even escaping from the North Sea.

Intelligence is the order of escape, so she must have been the greatest intellect of the North Sea to escape that wicked place in an instant.

Thus, Qing flung open the third door.

"Ah, ugh, ah, it's, good, ah, it's good. Kyaak!"

"Wh-Who is it!"

A couple, startled in the midst of their deed, hurriedly separated.

"Are you Carpenter Wang, Mister Jang?"

Then, a strange response came back.

It was a reply that came through telepathy.

-She said it's the fourth room. Can't you count? Not the third, but the fourth.

"Ah. Sorry. My mistake. Please continue with what you were doing. Ah, this door, why doesn't it close? I'm sorry, but please just focus on your business."

The dilapidated door had been flung open with such force that it had actually come off its hinges.

However, Qing was also an accomplished carpenter, recognized as a full-fledged member.

A carpenter sees as much as they know, and the apprentice carpenter's skills shone through.

Hmm. This is fucked. The door needs to be replaced.

I should prop it up inconspicuously.

It was then.

Gurgle, a small groan was suddenly heard, and Qing threw aside the door and immediately rushed into the next room.

Then, the smell of blood pierced her nose.

A man was sprawled on the floor, clutching his stomach. Blood was gushing out from the wound, pulsing with each heartbeat.

As an expert in human anatomy, it was clear that he was beyond saving.

Ah shit. I was one step too late.

It seemed his Evil Karma was high enough, so he must have been properly tracked down.

Since I'm already here, I might as well finish him off.

Qing was contemplating whether to crush his head, pull out his heart, or perhaps strangle him to enjoy the sensation of his last breath.

Seolganom came in, clicking his tongue, and placed his hand on the man's abdomen.

Could it be? Seolganom?

Even the greatest intellect in the neighborhood wasn't a complete all-rounder with medical skills.

He had simply frozen the wound shut.

The man's abdomen exhaled white smoke in the midsummer heat.

Seolganom let out a sigh.

"This should buy him about one quarter of an hour, at least. Now then. You. I'm listening. How did you end up hiding in such a wretched place, only to be stabbed by an assassin? Since things have come to this, tell me everything you know and try to secure a better afterlife."

"Keuheuk, secure a better afterlife, keuheukheu……"

The man, who was about to die, chuckled, finding the joke amusing.

Since the wound was frozen, there didn't seem to be much pain.

Seolganom shrugged at Qing.

It was a gesture to ask any questions she had.

"Hey. Mister Jang? Did you know the Naka River's embankment burst? Let's cut to the chase. Did you do it on purpose?"

"Like fuck I did. I just, skimped on some materials. But, keuk, yeah. It was bound to burst. Less than half the materials went in."

"Less than half the materials went in?"

"The design was so fucked up. I wish I could have seen the face of the bastard who designed it."

The carpenters had cursed, mixing admiration and profanity in a ratio of two to eight as soon as they saw the design.

It was well-made, but if they built it exactly as designed, there would be nothing left.

"So, what? Did you skimp on the materials?"

"As if. We saw the design and thought it was fucked up, but figured it was a chance to make a name for ourselves with a monumental project. Carpenters are like that, you know? They say they'll jump at the chance to leave their name on a major project, even if they don't get paid. Although, carpenters don't really lack for money in the first place."

Carpenters were, and are, a precious resource, even now or in the future.

"So?"

"But the higher-ups didn't see it that way. You get the construction funds, give some to the high-ranking officials, pay the workers, skimp on the materials, and pocket the rest. But if we followed the design, we'd be left with just a couple of gold pieces. Keuk, keuheuk, does that make sense? We managed to secure a flood control project, but it's not like we're some charity."

Jang said with a chuckle.

Since he was going to die anyway, he seemed intent on saying everything he wanted.