\chapter{Fire In Chang'an (5)}

The name 绿林(Lulin/ Green Forest) originated from a rebellion that took place in Lulinsan, in the ancient province of Hubei.

It happened during the Xin dynasty, a dynasty so short-lived, lasting only fifteen years, that it is not recognized as a proper dynasty.

It was established when the greatest saint of the West (fatherless) was a nine-year-old child and collapsed when he was twenty-four, working as a carpenter.

In Qing's homeland, the education system consisted of six years of elementary school, three years of middle school, three years of high school, and four years of university, totaling sixteen years.

Fifteen years might seem long, but in reality, it is a remarkably short period of time.

At any rate, Wang Mang, the first and last emperor of this Xin dynasty, was also famous as a rare idiot who received no positive evaluation except for his innovative attempts.

The word 망탁조의(Mangtakjoui) used to describe a traitor, tyrant, son of a bitch, or beast, has the first word, 망(Mang), derived from Wang Mang's name.

Wang Mang, Dong Zhuo, Cao Cao, Sima Yi. Mangakoi.

However, his innovative attempts transcended nearly two thousand years of time.

He was the first person in human history to implement the profoundly red ideology of prohibiting private property and establishing collective farms on a national scale.

As a result, this period of the Xin dynasty is considered the most catastrophic in Chinese history.

It wasn't just a failure, it was an utter catastrophe.

If only the Sword Master had studied Chinese history, he would have known that this was the very shortcut to utter failure and abandoned the red ideology long ago.

But alas, who would have been interested in the history of some pathetic people who collapsed after smoking opium? How unfortunate.

At any rate, this premature 'Arise!' fever had turned Zhongyuan very, very red with blood.

Thus, the first peasant rebellion in Zhongyuan occurred, which was the Lulin Rebellion. These were the predecessors of the Yellow Turban Rebels, the Lulin Army.

It wasn't that there had been no uprisings before.

But they were all cases where the aristocrats or the army had turned against the authorities, and the uprising of the Lulin Army was the first instance where the common people, realizing they were all going to die anyway, decided to pick up farming tools and take up arms instead.

As for the result, well, the fact that the bandits called themselves Lulindo speaks for itself, doesn't it?

At any rate, since the Lulin Army were also considered traitors, the name of Lulinsan was erased and replaced with the name Daehongsan.

However, although the name of Lulinsan was erased, the green spirit of Lulin remained in the hearts of the Lulindo.

Lulinsan no longer existed as a real mountain in Zhongyuan, but in the hearts of the Lulindo who inherited the spirit of Lulin.

This was why the greatest stronghold of Lulin, the headquarters of Lulin, was located on Mount Cheonja in Hunan.

Since Lulin no longer existed, there was no need to establish a base on Daehongsan (formerly Lulinsan).

It was definitely not because they were running away.

It was absolutely not because there was the Wudang Sect and the Shaolin Temple as neighbors, the Namgung Clan nearby, and even a government military base, Jumajeom, connected by a road, so that if the Imperial Palace issued a suppression order, thousands of cannons could be mobilized in just five days.

It was because Lulinsan existed in their hearts.

Meanwhile, Mount Cheonja was also a mountain beloved by the Han people, the roots of Qing.

It was a sacred place visited at least once in their lifetime by almost every Han person over middle age.

It could be said to be the spiritual mountain of the Han people and the home of their hearts.

However, they did not know the name Mount Cheongja.

Instead, the Han people called this Mount Cheonja by the name of Zhangjiajie.

Thus, Zhangjiajie! Mount Cheongja! The Greatest Stronghold of Lulin!

And there was a man who was the head of the Ten Thousand Lulin Strongholds (to the people of Zhongyuan, the number ten thousand meant 'all' or 'everything') and the Chief Inspector of the Ten Thousand Lulin Strongholds, whose moniker was Lulin Incarnate, Lulin Itself.

Lulin Incarnate, Wang Cheolgun.

That 'Lulin Itself' Wang Cheolgun was currently staring blankly at his son's corpse.

The body of his son, cleaned for burial, was spotless.

The body had been washed, the wounds stitched, and dressed in clean burial clothes, so although pale without the color of blood, it seemed as if he might open his eyes at any moment.

However, the dead do not open their eyes.

The heart of a father looking down at his son's corpse was not something that could be casually spoken of by those who had not lost a child.

Of course, if Qing had seen it, she would have just snorted.

She would have said something like, 'To think that the boss of a gang of robbers who makes a living by killing other people's sons and daughters, or other people's parents, feels sad about the death of his own child'.

However, wasn't it true that the pain of one's own hangnail was more painful than the death of another's child?

Therefore, although Wang Cheolgun's anger might not be justified, the level of his rage was reasonable.

"What did you say happened to Guiseon?"

"Ch-Chief."

"I'm asking what happened."

The Second-in-Command of the Greatest Stronghold, Bu Hyeolcheolgwi So Bangjeon, could only barely keep his lips moving, not knowing what to do.

Both shoulder blades and leg bones were shattered into powder, fingers were torn off, and one shinbone was completely exposed.

Even in that state, he did not die, so while writhing in excruciating pain from his crushed limbs, he was thrown into a puddle.

Unable to even turn his body, he eventually drowned with his nose submerged in the rising muddy water, so when he was discovered, he was already stuck in the mud.

The Chief ground his teeth.

"Isn't she a funny bitch? Butchering people like a butcher, robbing them of their gold and silver to use as her own, and even receiving praise for her relief work. If she's going to butcher people and rob them of their gold and silver, how is she any different from us?"

If Qing had heard this, she would have scoffed.

But Wang Cheolgun was serious.

"You said her name was Ximen Qing. Inform all the strongholds. I will give anything to the one who captures her. Even if they want the position of the Lulin's leader, I will give it to them. There is no need to capture her alive. Torture her to death in the most gruesome way possible. And bring her corpse to me. No, there is no need to bring it. I will go myself."

"Yes, Chief."

"All patrols and combat units are to focus entirely on pursuing Ximen Qing. If there is a stronghold that hesitates to act even when she passes by, I will personally visit and crush them."

The rage of a father who has lost his child freezes over coldly.

In fact, he seemed to have lost his reason, but he was also in a very rational state.

He did not extend his revenge to the Divine Maiden Sect or the girl from the North Sea, who had been said to have just stood there and taken a beating without doing anything. That was because if he had declared war like that, it would be the Lulin who would end up being destroyed.

Therefore, focusing on Ximen Qing alone was the same as saying to handle it quietly according to the internal rules.

The statement that he would give away the position of the Lulin's leader was also just talk. In truth, if someone without ability took the position of the Chief, they would soon face challenges and die a dog's death.

At any rate, he was the leader of a group that was renowned in Zhongyuan.

He was not such a pushover.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While someone was grinding their teeth and shedding tears of blood, Qing was completely engrossed in her tour of Xi'an.

Xi'an had attractions in all four directions.

To the east was the hot spring beloved by Yang Guifei, to the west was a thousand-year-old temple where the real bones of the Buddha were enshrined, Famen Temple, and the tomb of Wu Zetian.

To the north were the Bell Tower and Drum Tower, which served as the starting point of the Silk Road, and to the south was the Xingjiao Temple, which housed the relics of the second most famous monk in the world, Xuanzang.

For reference, the first most famous was the Buddha, and the third was Dalma.

Of course, Xi'an was vast.

Not just vast, but incredibly vast.

So, she couldn't make the effort to visit the attractions outside of Xi'an, and instead just wandered around the most bustling streets of Zhongyuan, buying snacks, eating, eating, eating, and eating some more while looking for key figures in the flood management project.

However,

"The owner got hit by a carriage, you know."

When she visited one house, the atmosphere was grim, and when she casually asked a passing servant, she was told that the owner had died after being hit by a carriage.

"Do you know where he went? He said he was going out for a drink, but he hasn't returned……"

One house had a person who went out for a drink and never came back.

"Aigo, aigo……"

One house was holding a funeral.

Someone went hiking on a rainy day and returned as a corpse with a broken neck.

Someone was last seen being dragged away by his opponent after trying to cheat at a gambling den.

Someone else died after falling ill from eating something bad, someone else died suddenly, and someone else went out and never came back……

Unless the heavens had inflicted a collective punishment on those involved, there was no way there could be such a series of deaths and disappearances.

Conversely, it meant that a person could do it.

"Ah shit. Should've come a bit earlier. They're all probably dead."

Because she was helping with flood relief, it had been a month, and since it took more than ten days to get to Xi'an, it had already been more than a month and a half since the incident.

Of course, she figured those who died probably deserved it.

They probably did something to deserve death, so it was fine that they died.

But this meant there was no way to know whether the Zhangheng Company had done shoddy work or deliberately sabotaged it.

Thus, Qing quickly moved from place to place, increasing her pace.

As she crossed off names from the list one by one, the sun set, and no names remained.

Hmm. What should I do?

This makes it seem like the Zhangheng Company definitely had something fishy going on, which is why they resorted to silencing everyone.

Of course, Qing wasn't particularly concerned.

She could just visit the head of the company and other individuals with high Evil Karma scores and have a sincere consultation session with them in the middle of the night.

However, if there were no individuals with particularly high Evil Karma when she visited, the incident would remain unsolved.

So she thought she'd collect some evidence beforehand.

But there was always someone nearby who was the best to consult on such matters.

Wasn't there Seol, the expert in sneak attacks, assassinations, kidnappings, arson, and nighttime ambushes, right beside her?

Seol would probably find the idea absurd.

From the beginning, Seol had never once thought of himself as a smart person.

He had no interest in or intention of being a strategist or advisor.

He was simply consulting with the smartest person in the area at Qing's whim.

At any rate, Seol, whose alias was Seol Garyeon, welcomed Qing, who visited him in the middle of the night.

"Visiting me at this hour reminds me of old times. Why did you come to tell me who to kill, like back then?"

"Wow. How did you know? You're a genius, Seol."

At that, Seol frowned.

"Was it not because the Demonic Cult killed people in the middle of the night, but because it was your hobby?"

"No. It wasn't like that. Actually……"

Qing shared the results of her investigation.

Seol stroked his slender chin and said, "Hmm."

But what's this? His beard marks are all gone?

Of course, Qing couldn't resist her curiosity.

"It's a side effect."

"What kind of side effect goes that far? Will your dick fall off later or something?"

"Fortunately, my dick is fine. It's been standing firm and proud every morning lately, which is quite enjoyable. Why? Do you want to check?"

"It's a bit unsettling with that face. And your voice too."

"My voice, well. Like this."

"Oh."

Qing expressed her admiration for the first time in a while.

The 'like this' part had a voice that was definitely that of a woman, albeit a bit husky.

"It's just a trick. You pick up things like this when you live as a fugitive."

"Oh. Can I learn it too?"

"It's easy for a man to imitate a woman's voice if you just learn the trick, but the other way around, you'd need to find a martial art that specializes in that. A woman's vocal cords are narrow, so it's done with Inner Qi, but widening what is naturally narrow is not easy. Hmm. Well, if you poke it, it might widen, right?"

"Ah. That way."

"If you poke it, it might widen, right?"

"Can't you just stop repeating the same joke? Also, your senses seem to have returned, so why keep up the act with the innuendos?"

"Just wanted to see your face turn red once. Why are you so uninteresting?"

"Well, I like raunchy jokes, so? Why? You gonna tell me some? Then I'm all for it."

Seol shook his head.

"When a woman is not shy, what's the point in seducing her? If she just strips and rushes in, even an erect penis will go limp, won't it?"

"Oooh. And then?"

"That's why your attitude is the problem. Hmm. Anyway, it seems like the Zhangheng Company has done something, so give me the list. I'll look into it."

"Can't we just kidnap suspicious guys from the Zhangheung Company one by one and ask them? That's why I came to ask you to tell me who the suspicious ones are."

Qing had come to ask who to kidnap and torture, like she did with the Demonic Cult.

Seol shook his head.

"The criteria for 'suspicious' is ambiguous, isn't it? It's not like you can just tell at a glance who's a bad guy. Plus, I've only been in Xi'an for less than fifteen days."

"Hmm."

I can, though.

Qing swallowed her words.

Seol skimmed through the list and scratched his chin, saying, "Hmm."

"It's likely that a few are still alive. Most of these key figures are probably close to each other. After all, they work on many projects together."

So when a series of deaths occurred, some would have fled.

Those who disappeared with their families or with their children definitely ran away overnight.

Of course, since it's hard to survive even if you run alone, those who fled with others would all likely die.

But among those who disappeared, those who ran alone to save themselves or to avoid implicating their families…

Whether they're sons of bitches or great parents, a few of those who ran away alone would have a high chance of still being alive.

Qing clapped her hands at Seol's explanation.

As expected of the local's top intellect!

And now that 'local' wasn't just any locality.

Wasn't he the top intellect of Xi'an, one of the largest cities in Zhongyuan?

This was why the wise men said to keep intelligent people close. 