\chapter{Fire In Chang'an (6)}

After taking the list, the Xue bastard naturally brought up another topic.

"Ah. By the way, That Guryeong. Hm. It really doesn't roll off the tongue to say Seol Riri."

"Are you two acquainted? And what's with this Guryeong? She's not exactly normal, but even so, how could you call a woman Guryeong?"

At that, the Xue bastard smiled bitterly.

"Well, it's not much different for any other clan. No, I should say it's a characteristic of any family-based village rather than just the noble clans. The Northern Sea Seong Clan, like any other clan, has a main family, direct lines, branch families, and collateral lines. If we were to compare their treatment, the main family lives like royalty, while the collateral lines live like ordinary people."

"And?"

"And below them are the bastards, or in Zhongyuan' terms, the illegitimate children, who are treated like commoners, slaves, or even animals. Anyone can freely order them around, and if they're bored, they can beat them. It's just that the price is a bit steep if you end up killing them."

Qing frowned deeply.

"Eh. What's that? How can they do that? It's been ages since slavery was abolished by national law."

"So, are there no slaves in Zhongyuan? Most well-off households usually have one or two, don't they?"

"It's because the national law is a joke. Anyway, they're just a bunch of jerks, acting all high and mighty just because they were lucky enough to be born into the right bloodline, talking about direct lines and collateral lines."

It was quite a rebellious statement.

But while it might be rebellious coming from Qing, it was also absurd coming from a princess of the direct imperial lineage.

However, the Xue bastard, unaware that she was a princess, just shrugged.

"Well, after thinking long and hard about why it ended up like this, I roughly understand. It's a kind of resource management, wouldn't you say?"

The Northern Sea is barren.

And it's not like there are many special products either.

There are fine quality furs, but the people of the Northern Sea barely have enough for themselves.

Of course, there are times when they can acquire such things.

However, no sect would carelessly export strategic goods just because they're hungry.

Just looking at the villages around Zhongyuan, the ones with iron ore mines dominate the surrounding villages. As such, it was only natural that they would never sell iron, no matter what.

Moreover, there aren't many merchants who come to trade with the Northern Sea. Even when they do come, they can't come during the summer because the ice is too thin, and they can't come in the winter because it's too cold.

With only brief visits during the spring and fall, the amount of grain they could buy from outside was minuscule.

The land of the Northern Sea simply could not support a large population.

Therefore, childbirth was strictly controlled according to bloodline. But in a land where it's cold and there's not much else to do, what else would they do?

They fuck like rabbits.

And as a result of fucking like rabbits, no matter how much they controlled it, children were unexpectedly conceived, and bastards were born.

"So, bastards can be used however one pleases."

Even if they weren't needed, bastards still had to eat and wear clothes.

Since they consumed the scarce resources of the Northern Sea, they had to work like livestock.

After all, they feed them, clothe them, and give them shelter, don't they?

As Qing listened to the Xue bastard's hypothesis, she thought.

Indeed, he's the most intelligent person in the neighborhood!

When he was in the Northern Sea, he was undoubtedly the most intelligent person in the Northern Sea.

"But they need to know who's a bastard to use them, so they give them bastard-like names from the start."

There was no effort made in naming them.

They just rotated a few names for boys and a few for girls.

For the three clans of the Northern Sea, Seol, Han, and Bing, the names for boys were Ganom, Jongnom, Gaenom, and Jotnom.

For girls, it was Ganyeon, Jongnyeon, Gaenyeon, and Guryeong.

"Ah."

"You asked if we were acquainted? There's a sect in the north of the Northern Sea called the Jade Maiden Sect. It's mostly made up of women. But that doesn't mean there are only women. Due to the nature of their martial arts, men tend to avoid it. Anyway, there used to be a sect called the Jade Maiden Sect."

Then the Xue bastard grinned.

It was the kind of smile a chef might make when hearing praise for the deliciousness of their food in passing, a smile full of pride.

"Of course, it doesn't exist anymore."

Wasn't it said that they killed everyone from top to bottom, burned down the sect's building, and then ran off with their Secret Manual?

He had also said before that although he thought he might have gone a bit too far, he didn't regret it. And that if he were to return to the past, he would do the same thing all over again.

"Guryeong was lucky. She was close to someone from the Ice Clan. That was the last time I saw her, being taken to the Ice Clan. Since she was being inducted into the direct line of the Ice Clan, she probably received a new name."

"Then, you were acquaintances?"

"In Zhongyuan terms, it would be like an uncle-niece relationship. But bastards don't have family records, so if I called her my niece, I would have been beaten to a pulp."

It was said that Seol Riri really did get beaten up every time he called her his niece.

But the kid was so damn stubborn that even though he kept getting beaten up, he never stopped calling her that. As such, it seemed he just ended up with a higher pain tolerance.

Hm. I think I know what kind of stubbornness that is.

As Qing nodded, she suddenly asked.

"Wait, so does that mean they sent her alone to this faraway land to find her uncle and kill him for the Secret Manual?"

"That's the pretense, but they just kicked her out. Guryeong knows it too."

"Eh? She knows? Why? Did you two talk? No, before that, did she even recognize you?"

"Of course. Don't I look exactly the same?"

The reason why there were men in the Jade Maiden Sect despite its name was due to the side effects of the Lunar Jade Maiden Divine Art, which gradually transformed men into the likeness of a woman.

Although the Xue bastard had overcome that side effect with the Ice Heavenly Asura Demonic Art, he lost his senses in the process.

However, he found that living without senses was hundreds of times worse than looking like a woman, so he used the Blissful Maiden Arts to purify the Ice Heavenly Asura Demonic Art and returned to his previous appearance.

In other words, when the Xue bastard lived as a slave in the Jade Maiden Sect, he looked the same as he did now.

"I heard they taught her the Ice Vapour Palm but not the more important Ice Vapour Divine Art."

Yet, she was still made to disperse the Lunar Jade Maiden Divine Art just because they said she had to learn the Divine Art.

As a result, only the Pathetic Arts remained, a pathetic Inner Qi Cultivation Technique that couldn't even create ice. With just that, her Inner Qi was no better than a First-Rate.

"Of course, the Ice Vapour Palm is a peerless Divine Art, but if I had studied it like that, how could it possibly display its full power? So if they told such a kid to capture a Demonic Adept who destroyed an entire sect, it's obvious that they were just kicking her out."

However, he had no idea why they kicked her out.

It could be that Seol Riri's talent was so outstanding that the direct descendants of the Ice Clan became wary and expelled her.

Or, it could be that her talent was just barely enough to learn the Ice Vapour Palm, making her a waste of resources to keep as a direct descendant.

The Xue bastard said that, but as soon as Qing heard it, she immediately made up her mind.

Looking at how that kid acts, they probably just kicked her out because she was useless.

"The direct line lives like royalty, right? Earlier, you said something about her being inducted into the direct line because of some Ice Essence?"

"Well, think about it. If a dirty, lowly beggar from god knows where suddenly becomes royalty just because they have some talent, who would acknowledge and follow them?"

"I guess so. That makes sense."

Qing didn't think of herself as a princess.

Because the dead princess had already died long ago, leaving behind only her body.

She felt sorry for the Empress, but it was a bit much to act like her daughter when she had just stolen her daughter's body. How could she possibly do such a thing?

"But why did she come all the way here to find you?"

"She said she wanted to see how I was living and maybe live together if I was doing well. So you should take good care of her. She seemed to follow you well."

"I've been taking good care of her, you know? I don't think it's possible to take any better care of her than I already am."

"Is that so? She followed you around all day. But still, keep a closer eye on her. Especially if she acts suspiciously, take her to a doctor. People from the Northern Sea don't usually express when they're in pain."

"Why?"

"Go to the Northern Sea and you'll see. In that harsh land, it's hard enough to take care of yourself."

In that land where blizzards raged, taking care of someone in pain was basically a death sentence for everyone.

So those who lagged behind were simply abandoned.

Since they couldn't expect help even when they were in pain, they had to grit their teeth and keep up.

As a result, they never showed any sign of pain.

Especially if they were bastards, because being sick meant they were useless.

If they showed signs of pain, it meant their condition was already severe enough that they were as good as dead. As such, they were treated as if they were already dead and their belongings were taken away before they were abandoned.

"So even when they're dying, they won't show any sign of pain."

"Eh. She did, though."

At that, the Xue bastard smiled a very soft smile for some reason, almost as if he was proud.

"That's possible, isn't it? Anyway, it's late, so you should go. Or do you want to sleep over? Just a heads-up, I have a habit of sleeping naked."

"You sleep with your clothes on, you know? You were wearing your top when you showed up, all drenched."

Qing snorted and replied.

"Hmm. Then should I sleep naked just for today? Wanna sleep together?"

"If you can't flirt, then just don't. Why do you keep making it gross by doing it twice?"

"One should always try twice. It's not polite to just do something once."

"Polite, my ass."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After doing some weeding and helping with the flood recovery efforts, her Righteous Karma had exceeded 4,000 Points.

Originally, she was going to learn the Wisdom Sword of Tai Chi through the Righteous Karma Exchange, but she had already reached the Transcendent Realm and evolved into Transcendent Qing.

As such, it didn't seem like there was a need to learn the Wisdom Sword of Tai Chi now.

When Qing searched for the Ice Vapour Divine Art in the Martial Arts Window, a purple-bordered Inner Qi Cultivation Technique was firmly in place.

Seol Riri said she was incomplete because she didn't have this. So, if I learn it and teach it to her, will she become complete?

Originally, Seol Riri practiced the Pathetic Arts and the Lunar Jade Maiden Divine Art, but because she had dispersed the Lunar Jade Maiden Divine Art, she was left with only the Pathetic Arts, which, according to the Xue bastard, was a pathetic Inner Qi Cultivation Technique.

It was impossible to rebuild a study that had already been scattered once.

This was because the dantian would naturally disperse the corresponding True Qi, since it would not accept it.

Of course, it wasn't like there were no other methods for Seol Riri.

There was always the Ice Heavenly Asura Demonic Art.

Even if its side effects were quite severe.

And it wasn't really possible to teach her the Blissful Maiden Arts either, since it was a Daoist art that purified miscellaneous energies, especially Demonic Arts, by making it pure.

Although both Qing and she practiced it, they were originally incompatible.

After reaching the Transcendent Realm, she realized that instead of learning various Sword Techniques, it was more valuable to learn a single Inner Qi Cultivation Technique that strengthened and nourished her Inner Qi.

If it was a purple-bordered Inner Qi Cultivation Technique, it was worth learning, even if it wasn't for Seol Riri's sake.

Or should I learn the Ice Vapour Divine Art and then ask to exchange it for the Ice Vapour Palm?

They were both purple-bordered.

I should ask Riri about that later.

And ask Master first.

The Xue bastard said he would investigate, so Qing didn't have anything else to do.

But it's not like she could just go around playing while someone was working.

So the idea that came to mind was scouting the enemy.

It was just a fancy way of saying that she would eat and drink while visiting the restaurants and teahouses that were said to be businesses of the Jangheung Trading Company.

After all, they were the enemy, and if there was anyone among them with a distinctively high count of Evil Karma, wouldn't they be the culprit?

So, she did that for a day. Two days. Three days.

Meanwhile, rumors that two peerless beauties were going around together spread throughout Xi'an.

It was truly the talk of the town in Xi'an, and in a way, it was also the talk of the town in Chang'an.

In both the literal and figurative sense, it had really become the talk of Chang'an.

As a result, men were particularly drawn to the streets on this hot day.

"Hm. I think I've seen that outfit a few times now."

When women chased after the Most Handsome Man Under the Heavens, they would stand very obviously and form a wall.

But men were different. They would either subtly glance while passing by multiple times on the same path or take a seat in the same teahouse and enjoy their tea endlessly while glancing over.

When Qing was in Nakseong, the rumors hadn't spread much yet, but a month and a half had passed during the flood recovery efforts, which was more than enough time for the news to reach Xi'an.

The Heavenly Flower Sword has appeared!

Some even called her the Most Beautiful Woman Under the Heavens, so they wanted to see if it was true!

Moreover, there were also rumors that she had three heads and a thin waist, so it was important to confirm whether she really had three heads or not.

In that sense, Qing did not disappoint the men's expectations.

However, despite that, there were no severe advances made, because who would dare to make a move on a Supreme Master who had reached the Transcendent Realm at such a young age?

No matter how beautiful one's wife was, no man wanted to be a beaten husband.

Still, there were some minor advances.

"That Young Expert over there sent this."

"Wow. How very kind."

Qing raised the bottle of alcohol and smiled with her eyes in response.

Seeing her hesitate to stand up, Qing shook her hand slightly to signal her refusal.

Regardless, for the three days of scouting the enemy's camp, the only money Qing spent was on snacks from street vendors.

This made it seem like some wicked woman who relied on her looks to mooch snacks, meals, tea, and alcohol from men.

But in reality, she was providing a rare spectacle of a peerless beauty's infinite meal.

In fact, she was providing a more rewarding sight than street performers, so it could be said that she was giving ample value for what she received.

And so, on the fourth day.

The Xue bastard finally spoke.

"I found one. Will you go yourself? Or should I send someone to capture and bring them?"