\chapter{Fire In Chang'an (2)}

If you have a crack in your bone, it really hurts a lot.

If you bump into something, your breath gets caught in your throat, and your body loses all its strength.

To what extent, you might ask? Well, if you crack a rib, it hurts just to breathe, eventually leading to tears. Then, upon realizing that crying makes it hurt even more, you just end up shedding silent tears.

Considering that Seol Yi-ri had cracks all over her arms, legs, and everywhere else, it's understandable that she had been hobbling around like a centenarian or someone critically ill.

But it was also amazing that she never complained about the pain and kept her mouth shut, to the point where one might wonder if she was even human.

"Weren't you in a lot of pain, even though you moved around like that? Does it still hurt?"

"Yes. A little."

She listened well when told to answer one by one.

Yes to the first question about moving around, and a little to the second question about pain.

With bones in her arms and legs in such a state, and her muscles just barely avoiding the level of melting off, how could it only hurt a little?

Then it occurred to me, wasn't this the same guy who didn't even wake up when his forehead was being seared in his sleep?

"Is that also a side effect of the Ice Arts? Your senses becoming dull?"

"Yes. Yes."

"But wasn't it because it hurt a lot that you were hobbling around? Huh?"

"No."

Then, why on earth?

Qing waited for her to continue.

But no further explanation came.

"Young Lady Seol. Usually, after that, an explanation of why you moved like a hundred-year-old man should follow, you know? It doesn't just end with a no."

"Moving slowly helps to heal faster."

Hmm. Qing tilted her head.

Considering she said it didn't hurt much, she looked like someone in quite a bit of pain.

It was one thing to move around, but wasn't she trembling and struggling to even hold a spoon?

The statement that moving slowly helped to heal faster sounded plausible, but the truth was, if one wasn't in immediate pain, they would just move as usual, according to habit.

Of course, Qing didn't hold back on her suspicions.

So, she poked her in the side with a finger.

If it truly didn't hurt, there would be no reaction even if poked, and if she was enduring the pain, poking her once would accurately reveal her condition.

"Eek!? Oof……! Hhh, huff……!"

Seol Yi-ri flinched and gasped.

Naturally, all her muscles tensed up at once, causing her to gasp for breath and curl up, making sounds as if she was choking to death.

And of course, there were beads of cold sweat forming.

At this, Qing narrowed her eyes.

"So it does hurt. You can't even breathe."

"Huf, guh, I can… endure it. Huff."

"No, but. If it hurts, you should say it hurts. Why are you trying to hide it?"

"I'm not."

She seemed to listen well, but when she started insisting, there was no backing down.

"You're not? Should I poke you again?"

"Yes. Yes."

"You said yes? Should I poke you again?"

"Yes. Yes."

In the end, Qing let out a deep sigh.

She was trying to die while saying 'poke me if you will'. Why on earth was she like this?

"At this rate, you won't even be able to move around."

"I'm fine."

"Enough. Since we're staying in the city anyway, just rest well during that time. Take off your clothes so I can apply the medicine."

"Yes."

And then she started struggling with her clothes, fumbling and moaning, using all her might.

Qing watched this and sighed deeply again.

"Ugh. Just stay still."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

I thought I would only stay while Keoltaran figured out the key technicians for construction, but once I stayed, I couldn't just leave.

The city was in ruins, and there was a shortage of hands, so what started as helping out for a few days turned into staying and helping out altogether.

Qing's superhuman strength was already beyond human.

Coupled with her status as a Transcendent Realm martial artist, she could do the work of thirty men by herself, so if she were to leave, it would create a significant gap.

So, what? Young Lady Seol's condition wasn't good anyway.

Since I'm helping, I might as well help to the end. Once I'm done in Chang'an, I'll just visit the Zhongnan and Wudang Mountains and quickly return home.

Honestly, Sichuan is a bit too far……

It's hot now, and it'll probably be even hotter there.

Thus, while staying in Nakneung, Qing's daily routine became quite diligent.

She woke up in the morning, roughly washed up, helped Seol Yi-ri with a quick wash, and then had breakfast.

This useless and incompetent wench couldn't even eat properly on her own.

Her hands trembled, showing clear signs of enduring the pain.

When Qing counted internally, it took her ten counts to bring a spoonful to her mouth and another ten to scoop a bowl of porridge.

She couldn't even hold chopsticks, so she couldn't eat dishes or vegetables, just slurping porridge and soup.

At this rate, she'd be eating breakfast until lunchtime and then immediately continue with lunch.

So what else could I do? I had to feed her.

Still, she didn't complain about the side dishes and ate well even when it was hot without needing to be cooled, just opening her mouth like a baby bird when given food. Hmm. She's kind of cute, though.

Seriously, if it weren't for her face, she would have been abandoned long ago to rot as a corpse somewhere.

But she just had to have a face that was my type, so whenever I look at her, my heart melts…….

After finishing breakfast, she would head to the flood recovery site.

There, she dug up the ground to retrieve corpses, cleared debris from collapsed structures, and helped lay new foundations and erect pillars.

At lunchtime, she would return to the firm to eat lunch and feed lunch to Seol Yi-ri, rest for a while, and then spend the afternoon helping with the recovery work in the mud.

If it didn't rain, they worked on reconstruction, and if it rained, they dug waterways, blocked and drained water, making rainy days even busier.

And this damn rain still poured down hard every now and then.

When the sun set, she would return, take a bath, and also had to bathe Seol Yi-ri, who would only sweat without doing anything, thus making her all sticky.

Last time, when left to bathe alone, she wasn't seen for a while, only to be found later, having fallen into the bathtub and unable to get out, swollen in the now-cold bathwater.

And then, apply medicine and change bandages.

Only after all that, it was time for dinner.

After eating and feeding dinner, just when she thought she could lie down, the old man would come and bother her.

"Aigo, my eyes are getting dim with age. There. That's right. You're sewing well. I thought you were just a brute with only brawn, but you have quite the skilled hands."

Qing was originally weak against the elderly.

She was even weaker towards those with high Righteous Karma.

And this old man's Righteous Karma was far from ordinary.

So, Qing ended up following his instructions obediently.

Turns out, he was a very famous physician known as the Wandering Physician.

A Wandering Physician referred to an itinerant doctor.

And ninety-nine out of a hundred itinerant doctors were quacks. Since they lacked skills, they couldn't settle anywhere, and because their medical practices had severe side effects, they ran away fearing the consequences, thus becoming wanderers again.

Therefore, 'Wandering Physician' was also a derogatory term that implied 'quack' or 'charlatan'.

However, this particular Wandering Physician was one of the rare ones among the hundred.

He wandered around to cities where epidemics had broken out or where major disasters had occurred, hence the title 'Wandering', and he offered medical treatment without asking for payment, thus earning the title 'Physician'.

So, Qing ended up playing the unwilling role of a medical assistant, falling asleep from exhaustion, only to wake up the next morning for another day.

Then, she would wash her face briefly and make sure that Seol Yi-ri, who had been staring at the basin of water and trembling, also washed her face thoroughly.

And then, off to the reconstruction site again.

"The Heavenly Maiden has arrived!"

"Oh my, Heavenly Maiden. Thank you."

"Wow, Heavenly Maiden! Heavenly Maiden!"

The neighborhood kids would sing the Heavenly Maiden song and follow her around.

For some reason, everyone in Nakneung would bow and rub their hands together, offering prayers whenever they saw Qing, practically treating her as a mobile shrine or Buddhist temple.

It was understandable.

From the perspective of the people of Nakneung, an unparalleled beauty suddenly appeared, offering food, bringing a physician, and then lifting logs the size of a person with ease during the reconstruction.

She was like a goddess sent from the heavens.

A Heavenly Maiden was a handmaiden to the gods, and since a Heavenly Maiden referred to a female deity, they were showing the highest level of respect by calling her Heavenly Maiden, to the extent they would even believe it if someone said a donkey was a horse.

To be precise, even if they didn't believe it, since the Heavenly Maiden said it was a horse, they would start to regard it as a horse from then on.

At first, when helping out, she was called Miss, Young Lady, Martial Artist, or Sir, with everyone using different titles.

But after the joint funeral where a memorial service was held, everyone started calling her Heavenly Maiden as if they had made an agreement.

The memorial service was rather makeshift, which made the title even more embarrassing.

Qing was somewhat a part of the Daoist community, and since she had helped Ximen Surin with memorial services several times, she could mimic the rituals.

She burned some paper money as seen, chanted some Daoist verses, danced with a sword, and roughly performed a clumsy imitation of wishing for the deceased to rest in peace.

But the city people didn't know any better.

And in the first place, a memorial service was a ritual for the living to find solace, not for the deceased to gain any benefit.

Thus, fifteen days passed.

How amazing is it that people get used to things?

Qing was now a novice carpenter.

She had reached a level where she could be recognized as a proper carpenter anywhere, as vouched for by the carpenters of Nakneung.

She had learned how to fit wood together without nails, so she could quickly assemble ladders, chairs, and beds.

Not with a 'bang bang', though.

Cutting wood with Sword Force made a 'whoosh' sound, and fitting it together with her monstrous strength didn't require hammering, so it just slid in with a 'whoosh'.

And yet, she was still considered a novice carpenter.

The path of a carpenter seemed more challenging than expected…….

Playing the role of a medical assistant also became familiar.

She could sew up wounds, set splints, and perform simple treatments with her eyes closed.

Her excellent senses combined with her manual dexterity meant she could literally do it with her eyes closed.

However, the old physician kept nagging her, saying she still had a long way to go.

The path of medicine was long and arduous.

From the perspective of a patient, caring for the pain of the sick, the Wandering Physician's teachings made her realize anew how difficult it was to save a person as someone walking the path of medicine.

And then, she would find herself flipping through medical texts at night, thinking she should study medicine.

As an extension of that, caring for Seol Yi-ri also became routine.

By now, she could skillfully wash and dry her, apply medicine, change bandages, and then feed her without spilling a drop on Seol Yi-ri's front.

It was quite a bother, but it was also rewarding.

Seeing a sick animal gradually open up to you was a touching experience, validated by various media in Qing's homeland.

From some point on, the way Seol Yi-ri looked at Qing softened slightly, showing a welcoming look, and she would greet her when she returned.

Three days ago, she even leaned on her first while in bed.

It was truly a touching scene.

She used to make a fuss about not being able to sleep if someone else was around, even desperately trying to find another room.

She used to complain every six minutes, saying that she didn't like the feeling of skinship and that it was hot, even though she was as cold as a bamboo wife.

But now, she was leaning on her own, showing a change akin to an episode of 'Our Child Has Changed'.

And on the thirtieth day…

Qing, now adept at washing, drying, and applying medicine, checked Seol Yi-ri's condition.

Martial artists usually healed quickly from injuries, and according to the Wandering Physician, Seol Yi-ri hadn't been severely injured in any one place.

By now, her bones should have set, albeit roughly, and her bruises had faded to a light brown.

"The bruises are almost gone, so you won't need to apply medicine from tomorrow."

"Yes."

"Alright. Shall we go eat dinner?"

"Yes."

Seol Yi-ri held out both her arms towards Qing.

Qing skillfully picked up Seol Yi-ri.

Caring for Seol Yi-ri had become completely natural for her.

Seol Yi-ri had also grown used to it, so in the morning when it was time to wash up, she could blow her nose well with a 'snort', and when being carried, she naturally leaned in and clung on. Even when being bathed, she positioned herself conveniently for washing.

So, just as Qing had become accustomed to caring for her, Seol Yi-ri had also adjusted well, making it progressively easier to care for he……

"Huh?"

Wait, something's not right. Shouldn't we not be used to something we shouldn't be used to?

And shouldn't the person who shouldn't be used to it not be used to it either?

"Young Lady Seol? You should be fine by now, right? I mean, there are only a few bruises left, so you weren't really in pain for a while now, were you?"

"Yes. Yes."

"Oho."

"Ah."

Seol Yi-ri seemed to realize it only then, letting out a surprised 'Ah'.

What do you mean, 'Ah'? You think just saying 'Ah' will make it all go away?

This is why people say that getting used to something is so terrifying.

Once accustomed, it becomes natural, and without thinking, one acts as usual, forgetting the original purpose.

Didn't Qing also used to receive care until it became natural?

When she was pretending to be a leg cripple in the Demonic Cult, her sworn sister used to dress, wash, carry, and put her to sleep.

Qing suddenly came to her senses.

Wait, why am I working as a carpenter?

And why am I happy to be recognized as a novice carpenter?

And what's with studying medicine?

Why am I naturally turning on the lamp every night and studying medical books?