\chapter{Fire In Chang'an (4)}

The coachman was truly putting his heart and soul into his work.

How could he not? The one in the carriage was none other than the Supreme, the future savior, and the cause of life, reason for life, and purpose of life, the Heavenly Demon Supreme, who had descended into the mortal world.

It was unclear whether driving a carriage was a task that required one's heart and soul, but it did use up a lot of brainpower, trying to avoid even the smallest bumps on the messed up roads filled with dirt and gravel.

The carriage of the Heavenly Demon Divine Cult was a supreme artifact embodying the most advanced technology in Zhongyuan.

With the coachman doing his best, there was no need to explain the comfort of the passengers within.

The only drawback was the heat.

In this era, heat was something individuals had to overcome through sheer willpower, not something that could be solved with technology.

So Qing overcame it.

She thought that Freezing Qigong was some useless thing that was only good for making cold Longjing Tea, but it turned out that the Blue-bordered skill was actually a supreme Divine Art with air conditioning capabilities.

This Pathetic Art, despite its name, had a surprisingly excellent effect.

And Seol Iri, instead of overcoming it, clung to Qing.

One could even say she was leeching off of her. Hm?

Qing suddenly tilted her head and thought.

The clothes she's wearing are mine. The carriage is also mine.

When I said I liked the horse, Geoltaran told me to do as I pleased and bought it for me.

The name of the smart horse that had pulled the carriage all the way to Naknyeong was Royal Butt. It was because when you looked at it from behind, the horse's butt was very much like a horse's butt.

For some reason, whenever the horse's name was mentioned, everyone's gaze would rudely turn to someone else's butt. What's with that? It's called Royal Butt, so they look at someone else's butt. These people of Zhongyuan.

Anyway, all travel expenses, food, and lodging were paid by Qing.

And to say it a second time, Seol Iri was a beggar without any spare clothes, not even a change of underwear, so everything came from Qing.

Food, clothing, and shelter all came from Qing, so what exactly does she do?

Isn't she just a literal parasite?

As Qing turned her head, Seol Iri felt her gaze and also turned to meet it.

Seol Iri was practically intoxicated by the coolness emanating from Qing, clinging to her tightly. As such, with their faces so close, Seol Iri's face filled Qing's vision like a full moon.

Seol Iri wasn't necessarily the most outstanding beauty among the Five Flowers of Zhongyuan, but the problem was that she perfectly matched Qing's tastes.

Seeing her face like this made Qing's heart soften.

That's when it happened.

"I want to sit on your lap."

"What?"

Now she even wants my lap as a chair?

Qing was flabbergasted, but Seol Iri quietly changed her words.

"Or you could sit here."

And then she patted her own lap.

Qing was not unaware of her intentions.

It was just that being close wasn't cool enough.

Qing placed her large ass on Seol Iri's lap.

"Haaah……"

With Qing, the source of the coolness, sitting on her lap, it was naturally cool.

A sigh of relief naturally escaped her lips.

And after some time, Qing realized.

This posture is pretty uncomfortable……

The seats of a top-tier carriage were top-tier as well.

It was only natural that the ride would be less comfortable sitting on someone's lap when there were seats that guaranteed the most advanced comfort in Zhongyuan.

Hm. She's not even useful as a chair.

How can every single day be a discovery of new uselessness?

"This is too uncomfortable."

Qing sat back on the chair, and then said, Ahhh, how comfortable, causing Seol Iri to look at Qing's lap with a gaze full of lingering attachment.

It was clear she didn't want to, but she didn't whine. She just quietly looked with such a pitiful expression.

"Agh, fine. Come here. What are you, a baby?"

"Thank you."

Seol Iri settled herself on Qing's lap.

She seemed very satisfied, letting out another sigh. And then, she leaned back naturally, putting her weight on Qing.

After all, with Qing's physical abilities, it wouldn't be much of a burden to have five or even more Seol Iri's on her.

However, this bitch… Her back is all damp…….

Then, Seol Iri started fiddling with Qing's hands, as if intending to warm them with the hypothermic effects of the White Hand Demonic Arts.

Seol Iri was a woman who deviated ever so slightly from the exact center of Qing's tastes.

Unfortunately, the woman who had pierced the exact center was an unspeakable bitch.

Anyway, since her type kept clinging to her, she started having indecent thoughts.

Ah shit, I can't hold back.

Qing reached out and stroked Seol Iri's collarbone area. Qing warned her.

"You're going to keep rubbing like that? I might just start groping you, you know?"

"Yes. Yes."

You're going to keep rubbing? Yes. I'll start groping? Yes.

"Huh? I'm going to grope you? I'm going to fondle you?"

"Yes. Yes."

"You're saying it's okay to grope you?"

"Yes."

"No, you're going to get into big trouble like this. Even if you don't like the heat, you can't just offer your body like that."

"You already groped me."

"Ah."

Qing was startled.

Back then, it was like a kind of explosion of worldly desires, or some pre-battle warm-up.

Was she even awake back then?

Wasn't she just knocked out from the medicine?

As Qing was about to apologize…

Seol Iri added.

"You did it every day, too."

"Huh? Every day? When did I?"

"Yes. Every day. When you bathed me."

"No, that's just because I couldn't just pour water on you during a bath……"

The clear color in Qing's eyes clouded over a bit.

"Hmm. No. You're right. Now that I think about it."

I took such meticulous care of her. Hmm. But still, hmm.

Yes. She's like a pet.

And since pets are meant to be petted, this can be considered a very legitimate exercise of rights. Yes.

If the various Buddhas and Daoist Immortals knew, they would lament that all their efforts to cultivate her compassion and mercy had been ruined by a foolish, ignorant, and lewd woman.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

If you follow Nakha River down, the next small city after Naknyeong is Naknam.

Nak was the Nak of Nakha River and Nam meant south, so it was a city with the very obvious name of being south of Nakha River.

And if you went west from Naknam, there was a huge road deliberately maintained by the government.

And if you followed that road for half a day, the largest city in Zhongyuan would finally reveal itself.

Chang'an! No, wait, Xi'an.

There are ancient cities in Zhongyuan called the Four, Five, or Seven Great Ancient Capitals.

They were the valuable lands of Zhongyuan since ancient times, where kings settled and became the center of a dynasty.

But if one had to choose just one among them, anyone under the heavens would not hesitate (except for those from Beijing, who would hesitate a bit) and pick Xi'an.

And Xi'an and Chang'an were the same city.

To be precise, Chang'an was a neighborhood within the huge city of Xi'an.

So, to be exact, Chang'an was not the name of a city but a neighborhood, like how someone from Qing's hometown would say Xi'an City, Chang'an District.

At any rate, Xi'an was such a city.

The fact that a piece of news that was popular and hotly debated among everyone in Zhongyuan was called the Talk of Chang'an showed the dignity of the Greatest City in the Central Plains.

However, it was also a city that was gradually declining, but even so, there were tens of thousands of households and over a million people living there.

One million people in a single city.

It was an overwhelming population that was unimaginable in the primitive and uncivilized ancient times.

Incidentally, this was also why the Emperor could gather an army of millions with just one command.

Even after the carriage entered the city of Xi'an, it continued for a long time without stopping.

It took another half a day to finally stop within the city, and when the coachman, 'Young Lady, I will open the door', politely opened the door for her to get off the carriage…

"No, what the hell is up with everyone?"

The sight that entered Qing's field of vision was countless numbers of heads stretching out towards her.

It was late August when the most revered and honored Heavenly Demon Supreme had personally visited the Solar-Lunar Inn, so everyone had come out to see the honored living god.

"No, do you people have nothing better to do? Tsk tsk. Can't you all just fuck off? Seriously, just openly, ahem."

A familiar voice was heard among them.

Qing's face brightened with delight.

"Gramps!"

"Tsk tsk. I received word that you were coming, but to think you'd crawl your way here now. You don't even know how to move around quickly as a woman. Aigoo, look at this. A woman as big as a horse should be ashamed of herself."

Qing rushed over and clung to him like a cicada, and Choi Leeong grumbled but lifted her up with a big, bright smile.

The old face was filled with wrinkles.

The members of Seolga Trading Company - Great Purity Merchant Association - Solar-Lunar Inn, which were essentially the same group, were surprised at the sight.

They had never imagined that the elder could smile like that.

Qing hung onto Choi Leeong like that for a while before skillfully sliding around to get on his back.

Then, an unfamiliar face came into view.

She was a very handsome woman.

How should I put it? Her features were distinct and her lines were thick, so she was a beauty, but she had a strong impression that made her look more handsome than beautiful.

"Ahem. You, it's been a while."

"Huh?"

Apart from that, a deep bass voice was emitted, and as soon as she heard it, she immediately thought of someone.

"What? You've become a total beauty. No, wait, your body type has completely changed."

At that, Seolganom's expression darkened.

"It wouldn't be called a Divine Art for no reason."

"Your boobs are pretty big too?"

"I just stuffed some things in there. It's actually flat in reality."

"What about your hips and waist?"

"That was a side effect. But it's much better than being a disabled person who can't feel anything-"

"Agh! I shouldn't be here!"

As she was abruptly cut off, Seolganom raised and lowered his eyebrows once.

"I heard you were coming-"

"No, that's not it."

As she was cut off a second time, Seolganom's eyebrows rose and fell again.

Qing urgently whispered, using half a Mind Transmission.

-Do you perhaps know someone called Bingseolhwa Seol Iri? She's been following me because she wants to catch Seolganom. But she probably won't recognize you looking like this, so just slip away now.

"Seol Iri? I've never heard of that name before. But my appearance is like this, so would she recognize me? And I'm using an alias these days because of my circumstances. You can just call me Seol Garyeon without worry."

"Alias?"

Seolganom, Seol Garyeon. Isn't that practically the same thing?

Should this be considered an alias?

"Surprisingly, it's a common name. You're just paying attention to that aspect, so it sounds that way to you."

"Hmm."

"Hmm. Seol Iri. Hmm. She must have realized, huh?"

"You know her?"

"She's coming this way. Let's talk later."

Seol Iri, who had gotten off the carriage, was looking around with an expressionless face.

But having been Seol Iri's caretaker, Qing was an expert in analyzing the Ice Flower's expressions.

That's not an expressionless face, but a nervous one.

And then she found Qing on Choi Leeong's back and her eyebrows very slightly, subtly, tilted.

That was a relieved expression.

Then she started walking towards them, but suddenly stopped with a very cold expression.

According to Qing's interpretation, it was a look of being at a loss.

There were strangers everywhere, but the only person she knew, Qing, was being carried on someone's back, so she didn't know what to do.

When she didn't know her, she was a cold beauty.

But in truth, she was just a seven-year-old kid with a lot of social anxiety.

Qing sighed deeply and jumped off Choi Leeong's back.

Tak, as she landed on the ground with the sound of her training shoes, Seol Iri finally moved and took her place next to Qing.

"Who is this grandpa? He's carrying my caretaker."

"……."

However, Seol Iri just pretended to not hear anything.

When Qing was wondering what was wrong with her, she noticed that Seol Iri was staring intently at Seol Garyeon's handsome face.

Feeling a prick, Qing poked Seol Iri's back.

"Ahem. Don't be rude. You have to greet Gramps."

"Hello."

"Gramps, this is Seol Iri. Ah. And where is my sworn sister?"

"Tsk. That one felt inadequate and useless last time, so she went into, uh, closed-door training."

"Hmm. Even though my sworn sister is helpful just by being there. I'm not asking her to fight, so it's not like I need her to shoot Sword Force or anything."

"Tsk tsk. She should at least not be a hindrance. I'm sure she felt something from that last incident."

"Still, I'd like to see her face. Can't I see her face if she's in closed-door training? Is she far away?"

"More importantly, aren't you hungry?"

"Ah. Now that you mention it, I'm feeling peckish. Did you prepare a lot? I hope you prepared a lot. What's for food? Is there any sweetly steamed meat?"

Choi Leeong skillfully changed the subject.

Qing's eyes lit up as she readily took the bait.
