\chapter{Yizheng Martial Study Hall, Opened (5)}

The final task of the admissions office was to organize the successful applicants into groups of ten to ascend to the Yizheng Martial Study Hall located halfway up Mount Baiyun.

"If you follow the Hongha Valley, even a seven-year-old child won't get lost, so even the most humble of people will find their way."

"But? Oh, but do you still need someone to stand in between roles? That's why you called me?"

"No, the Heavenly Sword goes up first-"

Suddenly, Qing clapped his hands!

"Ah, I think I know. You're only sending the officials up here, right? So, was this an attack after all? How did you know I'm so breathtakingly beautiful? I'll even strip your soul of yours."

"Huh? An attack?"

"Why, there's something like that. We also find out how well they can handle unexpected situations. And if they happen to run away and leave their comrades behind, they're completely disqualified."

"……?"

Sima Chunfeng frowns.

It's not that I'm offended, but rather because it's something I can't understand.

"The Thousand Flower Sword? Why did you come to that conclusion…?"

"Huh? You're a school official, so you can't even do that?"

Sima Chunfeng was speechless at that.

"How can we deal with an emergency when classes haven't even started yet? And since we haven't even had a formal entrance ceremony, aren't we not even colleagues, strictly speaking?"

The Uijeongmuhak-gwan was steeped in the selfish motives of the Wulin Alliance and has a strong political aspect, but isn't it still an educational institution?

At the very least, if it's an educational institution, they should teach something and then give you a trial. Even if they attack successful candidates who were climbing a mountain and find out how they handle it, what good will that do?

Of course, there were benefits to grading, but you should teach something before you grade it.

Besides, if you do that, only those with high skill levels and a lot of experience in the martial arts world will get high scores, so if that were the case, you would have just received them in order of skill level, and there would be no reason to receive them all from third-rate to the best.

"Is that so?"

"What on earth do you think of the academy?"

"All kinds of plots, raids, actual battles, bloody battles? And finally, a place where the world's greatest enemy can stop the destruction he dreams of and restore peace?"

"Keuheuk, that's not funny at all for a joke? Ah, the reason why Bone Sima-lang burst out laughing was because even the best swordsman in the world, Heavenly Blossom Sword, laughed at the joke because it was so bad, not because the joke was funny at all! Kkeuak!"

Sima Chunfeng, who had been stabbed in the side for the first time in a long time, jumped up.

As the weather gradually warmed, it seemed that even the steel-sided barbarian clothing was difficult to wear. Or perhaps he had let his guard down after not being stabbed for a while.

Anyway, it means that there will be no raid.

It was a bit of a letdown for Qing, who was considering whether to create a Shinto Vision Inpimyeongu.

Why, raids. They're fun.

"Ahem, I was just about to suggest that you, Sima-lang, should head to the mountain first. You have to inspect the facilities, organize the training unit, allocate lodging, plan outdoor training, and so on. Even if you're the only one on par with Sima-lang, the Heavenly Blossom Sword, this isn't the time to be taking it easy, was it?"

"Huh."

What the heck? What kind of organization was this? Why am I assigning accommodations? Outdoor training plans? And so on? What else was there to add to that?

Qing just blinked her eyes with that expression.

"Why was that? Haven't you been studying your lessons every evening? You even taught during exams, recruiting followers far and wide?"

The job of a swordsmanship instructor, as Qing sees it, was to go to the training center when there was time to teach, and when the time was up, it was over.

If I had to say, a part-time lecturer. Or a teacher.

But the teachings of the martial arts world were not meant to be carried out in that way.

If we have to say, it was an extension of the primitive ancient apprentice system, and each generation would teach the generation below them, and later on, they would have their own masters who would pass on the martial arts of the school and take their place.

Through this, within the sect/family, the seniority was naturally followed, and the elders were given fervent support, hoping that they will become their true teachers.

Of course, there were also disadvantages to this.

They say that the master only works hard to exploit you and doesn't teach you martial arts, and that there was almost no way to resist the evil deeds of the senior instructors, who were the real instructors.

Even within the so-called "Jeongpa" group, character and self-cultivation were the primary basis. In other words, they knew it was shameful in terms of reputation and morality. (Knowing it was shameful didn't stop them from doing it, though.)

But what about Sapa?

This was the main reason why factions did not last long, as they were seen as having a natural right and influence that should be exercised.

This was why the health of organizational culture was important.

anyway.

Only then did Qing realize her misunderstanding.

Oh, so you were a homeroom teacher, not an instructor?

If the total number of swordsmanship instructors was sixty-seven, how many were there even if you divide them into halves? If you divide them into squads, it's about six, so they're practically company commanders?

"Why were you doing that? Even though there were a lot of people, you could just take care of them like you did with your disciples at the temple. There were a lot of people, though."

It wasn't for nothing that the Wulin Alliance invited Qing as an instructor.

In reality, the first disciple teaches the second disciple, and the second disciple teaches the third disciple, so if it were the request of the eldest generation, wouldn't they teach the second, third, and fourth generation disciples?

It's actually not that difficult or complicated.

Because in martial arts, whether it's a group or a ronin, it's basically self-study and self-study.

It's a bit hectic when you first teach them martial arts, but after that, just group them together and let them train on their own.

After that, the upper ranks take turns in giving feedback on their achievements, and the lower ranks see each other every day, even if they only come out once a day since the private tutors take turns.

"By the way, isn't that really unfortunate?"

"Huh? What?"

Then, Sima Chunfeng smiles brightly.

As her eyes narrow, her tiny pupils and fierce squint were also hidden, so although she looks somewhat repulsive, she has a beautiful smile that was just plain beautiful.

Oh, right. This one was also a martial arts master.

It's a beauty that I've always forgotten because of the strangeness.

"Haha, it must have been Heavenly Blossom Sword's fervent wish to determine victory and defeat with Bone Sima-lang through a duel between instructors! However, she, too, dedicated herself to the military, intent on the well-being of the world, and so knows nothing about teaching. Since their respective contributions to the world differ, a formal event cannot be established. Haha, how regrettable that must be."

"Yeah, that's too bad. Oh, really."

What on earth was the official event?

Are you doing something like the National Sports Festival by yourself?

What was certain was that it doesn't help anyway.

Since you said you've never taught anyone because of your military service, well, I think it would be best to consult with other instructors.

South of Nosan County where the entrance exam was held.

Baekunsan Mountain was a mountain with a gentle slope at the bottom and a stern slope at the top, and it was a perfect place to admire the gray rocky peaks that rise up abruptly between the primeval forests that can be easily climbed to the middle.

So, its beauty was considered to be the best in Hanam.

However, when we say Baekunsan, we were referring to the entire Bokunsan Mountain Range, so it was only natural that a mountain range the size of a provincial city would be beautiful.

As I was climbing up the mountain trail, I followed the fairly thick stream, so it was a well-maintained path that was impossible to get lost on, just as Sima Chunfeng had said.

It's just a bit far.

It was about eighty li from Nosanhyeon to Yizheng Martial Study Academy.

If a healthy civilian walks on flat ground without any luggage, he will cover about twenty-five li in one hour.

Even if you climb the mountain path at that speed, it won't take you another three hours.

Moreover, the mountain road was not straight due to its nature.

However, even if they were third-rate, the physical strength of a warrior was far superior to that of a commoner, and even if they were second-rate, it was incomparable, so.

It's a distance that the officials can reach around dinner time if they leave after eating breakfast.

Since it was still a primitive era before the development of proper civilization (electronic devices), these ancient primitive humans were very good at walking.

Qingdo has long since been thrown into this primitive era.

Now, I've reached a point where I don't feel empty even without a screen when my hands were empty, such as before food was served, when I'm moving somewhere, when I have some free time and nothing to do, or when I'm lying in bed and can't sleep.

So, it's just a bit of walking.

My body feels so good, I can't even do this much exercise. Not only was my muscles not stimulated, but my breathing isn't even disturbed.

Now, whether I'm lying down or standing, walking or climbing a mountain path, I don't feel any different physically.

And no one cared about these things, and the mountain climbing had become a simple stroll, two people were walking on either side of Qing.

"Why doesn't Qing-ah shed a single drop of sweat?"

"Of course, since Heavenly Blossom Sword was a master of Hwagyeong. Phew, I wonder when I will be able to achieve harmony."

"Hey, Master Yuuk, you won't be far away either. You said you're facing Mount Tai?"

"I felt comfortable, like home, but now that the realm was blocked, I'm at a loss as to how I can ever reach it. It's still a long way off."

Yuuk-ah. He was a great disciple of the Taesan sect and was known to have reached the peak of his power.

In fact, he said that he volunteered to be a martial arts instructor in the hopes that he might get some tips since he had been unable to break through the barrier for a long time.

He was a master of the Taesanpa Vision Taesan Cheonrang Fist and was a very famous figure among martial artists.

To be exact, it was only famous among martial artists.

Taishan Tianlang Fist? That's kind of cool. Oh, it's gold.

Golden Boxing. Uncommon.

For reference, the Taesan of the Taesan faction was the famous Taesan, the Taesan that was familiar to Qing dynasty's Korean people, but the Taesan that was said to be high was this Taesan.

In fact, Taesan was much lower than Seoraksan, the sacred mountain of the Korean people, in terms of height alone, but because there were no other mountains for hundreds of miles around it and it was close to a vertical rock mountain, its imposing presence was actually the most impressive among the mountains.

This was why Taishan was used to mean the largest, most massive, and heaviest mountain.

Currently, Qing was on his way to the Royal Academy of Military Science with Peng Chaolei and Yu Uk-ah, meaning he was accompanied by instructors of swordsmanship, martial arts, and boxing.

"Where did we get? Oh, and how do we keep the people who were falling behind? Well, for that, you have to increase your own training time. You can't just feed them elixirs just because they're slow to progress. Even if you have elixirs, you have to give them to the ones who were good at it. And you can't have high-level warriors attached to you, right?"

"sure?"

"Well, you get treated accordingly. However, if you're a bit of a loser, they might arrange a marriage for you."

"Huh? A marriage proposal?"

"Once you have children, your passion changes, or should I say you become more desperate?"

"Haha, that's interesting. I guess responsibility was what makes a man."

Qing only worked hard to reform the Five Paths Sword Technique, but never even thought about the actual curriculum.

But? If you don't know, just ask.

So I was asking.

And I quickly realized that it wasn't as big of a deal as I thought.

If I had to say, it would be closer to the method of teaching beginners how to do it and then having them practice, or giving them a workbook and having them study on their own.

Pick a kid who's good at studying as class president and have them teach in your place, and things like that.

So, it's just that there were a lot of people, it's not a big deal that you're worried about.

The personnel composition was similar to the policy of whether to mix them evenly to improve the overall level, group them by level and manage them, or focus on only those who were good at it.

Come to think of it, I guess that's true.

Even though he was the great Transcendental Flower Sword Master, I felt like he was a bit lacking in talent to be assigned as an instructor right away.

But. Hmm. Isn't it a bit disappointing?

Still, it's only the Department of Political Affairs, and if everyone gains something, they should have pride and self-esteem as a member of the political faction. Even if it's not to the extent of living as a knight, well, what? Do you have any loyalty to the Wulin Alliance? It's not a company, but I think you'll develop a strong affection for it.

We've already selected all the successful candidates, and if we're going to waste the alliance's money and the alliance members' time.

If you're going to do it anyway, wouldn't it be better to do it properly?

After thinking about it for a while,

"You know. Well, then, we…"