\chapter{Yizheng Martial Study Hall, Opened (2)}

Applicants for this test could be roughly divided into several categories.

First, bamboo lovers.

The items to be destroyed started from bamboo and progressed in order of difficulty to wooden boards, iron bars, stone slabs, iron bars (large), and stone slabs (large). Among them, some of the test takers chose bamboo.

Some of them were applicants who chose items below their abilities, believing that if they challenged something, they would definitely succeed, and others were those who pursued the so-called safe option, as they said in Qing's hometown.

Or maybe it was just people who didn't want to stand out.

"Okay… Then…."

A woman in a tiger fur coat weakly raised her back and trudged away, leaving behind a single blazing bamboo stick.

It was a demonstration by the tiger fur woman Che Yaohong.

Of course, it might have been difficult to melt stones or iron by swinging a fire fist or fire leg.

Still, you could say that just burning a single bamboo stick was a bit insincere. It's a bit much to just light a fire and turn around.

In other words: Hmm, it would be convenient to light a fire.

The shelf life of a firestarter sticks display was rapidly decreasing whether you use it or not, and it's a useless luxury item, so it's hard to find outside of big cities.

And the next type, the one that took up the largest proportion of applicants, were the ones who wanted to show off.

Of course, the thirst for attention was a basic nature of a martial artist, otherwise where would the reward be in the arduous training of martial arts?

So, it wasn't something to frown upon or deduct points for saying 'that's too much'.

And if they succeed, wouldn't it be a chance to make their name known in front of this large crowd?

"Please erect four stone slabs."

The crowd was filled with exclamations of anticipation and excitement.

Not one, but four.

That's right, Azure Dragon Dancer Cai Shengxia.

With a large dance line that was even more amazing than their skills, they swished the wind around energetically, and then a fierce crashing sound was heard.

At the end, a blade of wind was drawn horizontally, and all four stone slabs were shattered.

"Azure Dragon Hero!" "Azure Dragon Hero!"

The voice of the cheering voice got louder, and he lft the room pretending not to care, but with the corners of his mouth twitching slightly.

Even as his chest pounded with anxiety, he met Qing's gaze with a proud look in his eyes as if to say, "How did I fare?"

\textit{Hmm, that attitude is kind of cute.}

Qing was an Unrestrained Realm master, and a fraudster armed with all kinds of Divine Arts.

If you gave Qing four immobile stone slabs, she'd just pull out Sword Force and cut them.

It's like a five-year-old struggling with all his might, shouted 'five times three is fifteen!' and then bragged to an adult.

Multiplying at five would be something to be proud of, but was that even a skill?

\textit{Well, I think he'll do well in graduate school. No, I don't know he'd get a job, but I think he'll do well in graduate school.}

And there were applicants who were blinded by their levels, or who had no self-awareness and only had grand ambitions.

For example, the nobleman Wan Talu of Sichuan.

"Stone stele."

'Give me the stone stele' he said, his arrogant demeanor uttering two words as if it were a given.

'Is the stone stele your friend?'

'Do you think the members of the Wulin Alliance are your servants?'

It seems that he was either an arrogant nobleman or he was too immersed in pretending to be an arrogant nobleman.

Surprisingly, there were many people who tried hard to imitate eccentrics in order to become famous.

Even without going far, weren't the actions of the Sapa guys, who act like real men, pulling out knives when you bump shoulders, and flipping over food when it's late, all just an extension of this?

Since when the term 'manly man' became synonymous with anger management disorder?

Perhaps he had gained a female admirer, perhaps it was because of his attractive appearance, but a scream similar to a woman's characteristic 'Kyaaa' resonated.

Wan Talu bent his knees, lowered his center of gravity, and grasped the hilt of his sword, glaring at the stele in a rather impressive manner.

To Qing, it was a perfectly cool a pose that looks.

"Hmm." "Hmm."

It seems like everyone felt it, as groans were heard from the left and right of the judges' table.

And the result. Bang!

With a dull thud, half of the blade flew through the sky, spinning around, and then, bang, it plunged deep into the ground.

Everyone was convinced by it at once.

"Oh, my." "It seems he put too much trust in the sword." "It looks like an expensive sword. What a shame."

It would be impossible for a broken blade to floated up and gets stuck in the ground unless it was sharp enough.

Sure enough, a blue sheen was briefly visible refelcting off the blade, so it must have been a type of sword called Qingchang sword.

It was also the name of one of the famous swords used by the most famous general of the Cao clan in the past.

Even now, over a thousand years later when the forging technology of Zhongyuan has advanced, it was still a treasured sword with a terrible yield, with only about one in ten swordsmiths able to produce it if they put in the effort.

"Damn it!"

Wan Talu threw his half-sword and walked away, grumbling.

It seems like he confidently challenged himself, trusting in his equipment. Too bad. He only lost his sword.

And finally, there were people who judged their abilities very accurately.

Sword Jade-lady neatly cut down the iron bar, eliciting exclamations of "As expected of a sword!"

The suspicious, squinty-eyed man who had been blocking Cai Shengxia's ugliness, Zhang San, also cleverly displayed his skills by cutting three stacked wooden boards.

As for the test takers who best understood the test's intent, their abilities were already roughly estimated in the first test, so if the test takers weren't hiding their strength, it would have been the same.

Rather than that, the examiners were focusing on attitude, whether or not they'll cause an accident if they're taken in as a member of Wulin Alliance, and whether or not there'll be any talk about it later.

In that sense, the Sichuan nobleman has probably reached a point where he's completely lost. You can't join us? Have you failed to survive?

I don't think there will be any trouble at Yizheng Martial Study Hall.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The test taker's accommodation is, of course, a group room.

How many applicants were there? Do you think they should all be assigned to a room each?

And since those who had the time already unpacked their luggage in the guest room, it wasn't particularly inconvenient for the test takers to use this group room.

So, at first, you unpack in the room you come across, and as the test takers become close to each other for whatever reason, whether it be their background or personality, they end up sharing a room with those who were close to them.

In the dormitory for the applicants for the entrance exam for Yizheng Martial Study Hall, room 15.

The room was completely dark when the sun has not set yet.

Well, with the curtains drawn all over the windows and doors, it couldn't possibly be not dark.

In that dark room, several people were whispering and talking.

"There's one Unrestrained Realm. Eight Transcendent. What about the other applicants?"

"It's not much, but there seem to be a few people we need to watch out for. First of all, that Azure Dragon guy, and that Sowd Jade-lady woman, she's no ordinary one, and that fire-breathing woman, too, isn't she?"

"If you gently tease him, he'll easily fall for it. As for the women, just be careful not to incur unnecessary hatred. And what else?"

"There's a rumor that the ronin from the Hidden Dragon Competition have arrived. It seems like they've become quite famous among the ronins."

"By the way, can we turn on the lights? Why are we talking in the dark—"

"Quiet."

That's why. It's much better to put your feet down and put up a curtain than to have a single layer of door to insulate the sound.

And there were psychological reasons too.

Originally, a conspiracy was made in a dark and confined place to be stable.

You shouldn't share treasonous stories in a bright, open place because others might hear them.

"The Demon King wants revenge. Those vile hypocrites treat our people with the utmost horror, so we'd better refrain from doing anything even slightly suspicious."

"Isn't this even more suspicious?"

"Even if you block out the light, what about the smell of burning oil? If you suspect someone was inside, it wouldn't be strange if someone started eavesdropping for no apparent reason."

"Indeed, Master Duan Dio, you have a plan for everything!"

"Quiet. Your voice is too loud."

The man called Duan Diao frowned and cut off his subordinate's words.

This was the situation that the Blood Cult's Heart Ritual Group was currently facing.

There was no talent, no talent.

The Blood Cult was made up of those who were persecuted by Zhongyuan, or the descendants of those who were persecuted. How could proper education be possible in such a situation?

Those who had been properly educated, had sharp minds, and were equipped with strong mental armament had already established themselves in Zhongyuan in the form of the Blood Net Gate sect.

After the Hangzhou disaster and the destruction of the Blood Net Gate sect, they faced a serious shortage of talent.

"Don't be complacent. It's for the sake of our cult, but it's also for our own protection. Have you forgotten the atrocities those hypocrites committed against Lady Demoness? Even animals can't be boiled alive, so they will treat us worse than animals."

Qing, who was actually boiled alive, must have felt wronged.

The reason we don't boil animals alive was because if we don't drain the blood and remove the internal organs before slaughtering them, they will become inedible.

And it's true that those Blood Cult bastards deserve to be treated like beasts. What's wrong with boiling them a little?

Duan Diao gritted his teeth.

Young Lady Demoness Yuryang was not a good boss to begin with, and to put it bluntly, she was a complete bitch.

But that doesn't mean she deserved to be treated so cruelly.

It was what the hypocrites of the Orthodox, no, the entire Wulin, no, the entire Zhongyuan did to them.

And now was the opportunity for revenge.

The opening of Yizheng Martial Study Hall was transparent and its purpose was clear.

The Blood Cult's activities were expected, and the Sado League has continued to gather strength since the Great Emperor Mucheon, so it will become stronger today than yesterday.

As far as the leaders of Wulin Alliance knew, even the Imperial Palace was suspicious.

So, Wulin Alliance needed to unite more than ever and grow in size.

The opening of Yizheng Martial Study Hall was for that purpose.

But what if that recruitment failed?

What if, not only was it ruined, but a massacre occured, killing and injuring countless people?

What would happen if even the precious young masters who were considered successors among Orthodox Wulin top sects could not be protected?

Above all, there was the Heavenly Blossom Sword, an enemy who they cannot be satisfied even if she was torn to pieces.

Heart Ritual Group lost a significant number of the blood demons they had worked so hard to create due to the Hangzhou disaster.

Blood Maws, monsters that simply crave human flesh, could be mass-produced easily, but Blood Demons capable of thinking on their own could not be created in a short period of time, so the damage to Heart Ritual Group collapsed to a level that was impossible to recover from.

This humiliating infiltration operation was also part of that.

The terrible humiliation of having to wag your tail and eat the pieces of meat thrown to you by those Zongyuan hypocrites.

Henan Province was the front yard of Wulin Alliance, and with their current strength, they cannot attack the Yizheng Martial Study Academy from the front.

Therefore, in response to the just revenge of the school, volunteers was selected as a moles who would burn the enemy from within!

However, they lacked the qualities of a warrior.

But it doesn't matter.

Although their qualifications were somewhat lacking, they have gathered volunteers who were diligent in carrying out their duties.

That was why he, the strategist of Heart Ritual Group, the closest aide to Heart Demon King, and the brains of Heart Ritul Group, would step forward himself.

Duan Diaoya smiled coldly.

In his eyes, a bright blue light bloomed, filled with hatred.

Duan Diaoya had always been kind and polite, so it was a thorough disguise that anyone who knew him wouldn't recognized him.

Who in the world would doubt him?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Sima-lang? That candidate named Duan Diao, he was on this test this time too. Didn't you say you were going to check his background again?"

"Kuhuhuhu, there's no need to worry, is there? The premonitions of geniuses like us—geniuses, with their supreme five senses, connect their upper and lower bodies with the will of Heaven—can't be ignored, right? The results will be announced after all exams were completed, so any applicants who find the results questionable, as advised by the Heavenly Sword, will not be able to participate."

Qing's heart also felt a little uncomfortable.

\textit{Since Evil Karma didn't necessarily guarantee they're bad people, it may just be that they ended up failing.}

\textit{But can I just ignore it?}

"Hmm. That might be a bit much."

"Oh, Heavenly Blossom Sword. Aren't you care too much about those ordinary people? Tsk tsk, how weak you are. In the footsteps of giants like us, who must accomplish great things, there are bound to be insignificant beings who are inevitably swept along. How can we possibly carry out a great cause if we can't walk for fear of stepping on an ant?"

Qing knew that Sima Chunfeng, who spoke like a villain, actually provides generous compensation even when she uses just one of Alliance's servants.

\textit{The kid is a good person, but why does he say things like this?}

"It's been decided that Yizheng Martial Study Hall will open next year, and they're saying they'll consider the year after next based on this year's results. Oh right, this is still confidential, okay? They'll announce it on the day the successful applicants are announced. If they're so inclined, they'll reapply next year."

"Oh, really? Then what?"

It was a statement that made her uncomfortable feelings feel a little lighter.

As expected, smart people all have plans.
