\chapter{Yizheng Martial Study Hall, Opened (7)}

It was an unexpected declaration of disappointment.

Unlike in Qing's homeland, the authority of the instructors of Yizheng Hall was immense, so the silence was immediately filled with the sound of cold, rolling eyes.

Qing felt very satisfied.

\textit{Oh, this is it.}

\textit{I made them notice!}

\textit{I can rule them!}

\textit{So that's why the company sergeants were always disappointed.}

\textit{I was wondering why they were always disappointed, why was it that they were in a profession that was prone to disappointment, and why they taught me to be disappointed in everything in conscription training.}

Qing pretended to add an even colder voice to the chilled atmosphere.

"The director has willingly shared precious words that will guide our life, truly golden principles, such deeply moving lessons. Instead of shouting out your gratitude, what's that weak voice! Louder! With the determination to tear down the heavens with your voice! Or have you skipped dinner!?"

Shee turned her hand around in an exaggerated but elegant gesture, then pretended to lean it against her ear.

It's a playful attitude, as if no sound was heard.

Well, it's a bit difficult to establish military discipline from the first day.

Since it was not the military in the first place, there was no reason to enforce military discipline, and it will not be too late to control discipline after seeing how the academy discipline is.

So, it's an untimely imitation of a drill sergeant.

Only then did the officials' frozen expressions loosen, their eyes fixed on each other, and each took a deep breath-

"No!!" "No!!" "No!!"

"Or are the officials of the world's best military academy exhausted from the long daylong hike!?"

"No, no!!" "No, no!!"

"Then, with a heart full of respect for Director Yu, who has given us such precious teachings, let's shout out loud to the front and fire as much as we are grateful!"

"Wow!!" "Thank you so much!!" "It was really touching!!" "I respect you!!"

And the outpouring of passionate support.

A shockwave-like response that shook the earth and even shook the stage, showing off its majesty as if the previous cheers were nothing special.

Dagger Sword Commander Yu Shan-ye's pupils dilate.

I've heard people say they talk too much all this time, but it's all for their own good, and I'm asking you not to do the same thing that I regretted wasting time on living so long.

Of course, I knew that many of the officials seemed bored and tired, but I also knew that the voices were coming from Heavenly Blossom Sword.

Yu Shan-ye stroked his beard with a look of satisfaction on his face, the corners of his lips parted.

Heavenly Blossom Sword has become a very famous person, these days, people were anxious because they can't stand out, and they don't know how to serve their elders.

No wonder all the elders unanimously praised him. He's a monster, a monster.

It was a very unreasonable phenomenon where the sound was given by the officials but the praise was given to Qing.

Yu Shan-ye, who had been enjoying the countless applause and cheers pouring down on him for a while, raised his hand to signal that enough was enough.

Only then did the voices begin to die down.

Qing took the ball with a big movement.

"I've heard the spirit of the officers! The Lord has already spoken well, so any further comment from me would be superfluous! Now, I've gathered here on both sides of me, instructors more admirable than I, but seeing these imposing officers, my heart races with excitement. So, at the risk of being rude, I'll introduce myself first!"

And then, hmph.

"I'm Ximen Qing! I've been appointed as your swordsmanship instructor! And the sword is truly the ultimate weapon, the king of all weapons! I can only imagine how much you agree with me by the sheer volume of your voice!"

Those who applied for the swordmanship course were screaming and yelling like they want to shout so much today that they will lose their voices forever.

And so the frenzied shouting ended.

Peng Chaolei and Yu Uk-ah exchanged glances and quickly reached an agreement, with Peng Chaolei taking the first step.

"Hang in there, you idiots! The sword is the king of all weapons? That's something I can't ignore. After all, swords are weapons only the savages use to show off. Would a true warrior with the sword be pushed around by their sense of duty? Well, the dao is the ultimate weapon! Isn't that what everyone thinks!?"

Then again, Kkaaaak! It seems that the number of dao trainees was small, but those who uses dao naturally have loud voices.

After another round of shouts like that, it was finally Yu-wook's turn.

"I'm Yu Yu-ah of the Taesan School, teaching martial arts. Isn't this a weapon technique, a trap for the weak who must wield weapons? A truly strong person was strong in and of themselves. I will hear the spirit of the martial arts masters here!"

I don't know since when the word 'uigi' started to mean 'voice'.

The funeral ended with a huge noise in the middle of the night, causing great psychological damage to the beasts on the mountainside.

But it's okay because it's a mountainous area with no houses. If the author had done it, it would have been serious noise pollution that would have called out the authorities.

After the meal, the school guards in charge of security, operation, and support of the school lead the students from each department to their dormitories.

A six-person room with six beds on each side, and a large personal locker, although old, was spacious and appears to be faithful to its purpose.

Because it was a mediocre accommodation, neither particularly good nor bad, the officials' impressions were also indescribably subtle.

I'm not sure if I'd say it's disappointing, but I'm not sure if I'd say it's good either. Well, it's just a place to stay. It's a place to stay.

Someone immediately starts snoring loudly, someone else realizes that they were meeting the wrong person and says, 'That kid snores really loudly,' and someone else mutters.

What kind of martial arts do you think I'll learn? He's the famous martial arts academy, so he'll teach you some decent martial arts, even if it's not quite divine. By the way, the Heavenly Blossom Sword was beautiful. It's not for nothing that people say it glows. It just suddenly catches my eye…

And so the first day of the State Affairs Academy passes.

All I did was listen to Santada's sermon and scream until my throat was hoarse.

Still, everyone was filled with excitement and anticipation, thinking that it was just the beginning.

The school bell was ringing, wake up now!

The reason why the original training center was located in the mountains is, firstly, the land was cheap (permission was easy to obtain), secondly, there was nowhere to run away, and thirdly, it was free from complaints about noise.

Whether it was Zhongyuan or the hometown of Qing, the sound of a large temple bell rings majestically out of nowhere from the morning.

And with him.

-After everyone has finished breakfast and washing their faces, gather in the main hall within half an hour!

Outside, the shouts of the Wulin Alliance warriors resonate loudly.

It's not that the warriors' voices were loud, but rather that the soundproofing of the dormitories in the Yizheng Martial Study Academy, which were originally built with the summer semester in mind, was poor.

Here and there, moans like "Ah …

Now that I've just woken up from a night's sleep, of course I'm feeling a bit dazed, my body was a bit heavy, and I'm scratching my head with my eyes half-open.

The student dormitory. That is, the staff quarters were single rooms, each with a spacious bed, closet, table, and chair, and even have hanging calligraphy to add a touch of style.

It may not be a very spacious room, but unlike the six-person dormitory, where else can you find an environment that guarantees privacy?

The sound of the Deengdeng temple bell ringing from early in the morning.

A bell rings faintly, carried by the wind, from afar. A clear sound echoing in a dream…

I wake up from my deep sleep and become conscious naturally.

It was a refreshing morning.

Of course, there was also the reason why he slept in a better room and bed than the officials, but Qingdo was a Taoist priest in his own right, in fact, a high-ranking Taoist priest among Taoists.

For members of the Taoist and Buddhist sects, the start of the day was the sharp dawn, the dim blue sky before sunrise.

"Should I sleep?"

The one who lies down with his soft flesh on top of Qing body.

You might wonder if it would be okay for two people to share a room, but most educational institutions in this era were private, and the people of Zhongyuan were originally very tolerant of 'us'.

Anyway, the boys' club was more like a summer training camp that focused on fostering friendship rather than achievement.

"Sleep, sleep? Sleep, don't sleep? Sleep, sleep, don't sleep?"

The child's body trembles slightly.

Well, Qing was a true master, and a true master has the mysterious, powerful, and truly omnipotent power to tell whether a child was pretending to sleep or really sleeping just by listening to their breathing.

And it's not like it's been a day or two since Ciyu woke up and pretended to be asleep while hugging Qing.

"I think I just laughed?"

"Sleep, sleep."

"This? You're lying all along?"

Qing hugs Ciyu and tickles her.

The child's face, which had been bright since morning, burst into laughter, hehe, hehe. The somewhat gloomy and cloudy laughter was like a speck of dust on jade, but anyway.

And next to him, a woman who was sleeping soundly, oblivious to the world, was Xue-i-ri, who eventually gained the unprecedented position of a foodie at the State Council.

He showed up without being summoned by the Wulin Alliance, and he refused to take on the role of leader, but he followed Qing up as if it were a given.

Qing thinks this was okay, but according to Sima Chunfeng, it's still the Five Flowers of the Martial Arts World, so even if it doesn't do anything special, it'll still be helpful.

Well, then, what would you call that in Western dialect, in Zhongyuan? A shaman statue? Anyway.

Even within the same fenced-off building, the morning scenery showed a dramatic difference.

But what's wrong with treating members of the Wulin Alliance well when the organization was investing money and manpower in a business?

If it were the hometown of Qing, it might have been controversial, but this was still a primitive society and such things were quite natural in ancient times.

Why, whether in the East or the West, do we bother to record the events of generals dining with their soldiers? "Look at this! A master eating with his servants, even socializing with them!?" "Wow, that's incredible!" This was truly an astonishing achievement, an unbelievable feat! It's a time when we insist on leaving it for posterity.

The officials were not open, so they shove breakfast into their mouths with half-closed and half-open eyes, not even knowing what it tastes like.

In fact, even if my sense of taste was awake, I wouldn't have known what it tasted like. Because it wasn't that tasty, but it wasn't bad either.

Then, they gather at the main military camp to receive the first morning assembly and the daily assembly ritual training that will be held from now on.

You might ask, what kind of roll call was this in a school? However, it was the most effective way to count the number of people in a group, and it was a human wisdom that has been passed down since ancient times, regardless of East or West.

And then, Qing slowly steps into the student affairs office cafeteria.

Morning roll call? I don't know about that.

Because the instructor was the one who taught, not the one who took roll call.

The four instructors savor the food prepared by the expert chef of the blind since morning, and have time to chat about future training.

When I saw the sound of the slogan "one, two, one, two" coming from outside, I thought, "The officials were really diligent since morning. What could be better than running to warm up in the morning?"

Then, the boy's instructor, Weifeng, leaves first to check the number of boys in the boy's department.

Since the boys' club was already members of the Wulin Alliance, they didn't bother to do a roll call or act stiffly.

Then, the sun slowly rose and the day became bright, so only then did I head to the swordsmanship school for my first class in Qingdo.

It was the official opening of the State Affairs Academy.
