\chapter{Yizheng Martial Study Hall, Opened (1)}

After finishing the first test, she rested for a day and then woke up, or to be exact, she was still sleeping.

-Sister! Sister! Are you there!?

"What."

Being woken up early, Qing let out a sharp reply.

If it weren't for the fact that Ciyu was lying with her head on Qing's chest, she might have blurted out some bad words, but Ciyu was also a light sleeper, so she woke up and looked up at Qing in a dazed manner.

"Children don't wake up in the morning. They sleep more."

"Ciyu still sleeping?"

"Hmm. Changming, that rascal."

\textit{If I were to ask Ciyu she's acting cute, she'd probably say that Little Mom taught her that.}

\textit{What does she keep teaching the child?}

\textit{I'll let it slide though, because it's really cute.}

"Okay. Ciyu keep sleeping."

"Ciyu sleeping, sleeping."

Chen Changming's style cute face, or a noble face.

\textit{No, really.}

\textit{If you keep doing this, I'm really starting to like it.}

\textit{Changming'er know my tastes so well.}

Qing-i smiled and placed Ciyu on top of Xue-i-ri, who was lying next to her.

Ciyu didn't like the height of her new pillow and was finding it uncomfortable. She's trying to find a comfortable position by resting her head here and there.

But once Iri fell asleep, she will never wake up.

\textit{It seems like she's uncomfortable, her forehead wrinkled slightly, her eyebrows were slightly furrowed, and she looked very suffocated, but, um, I wonder if it's okay for a martial artist to sleep this deep.}

Qing, dressed roughly, left the guest room.

It might looked sloppy, but it's a very refined clothing technique that she had been practicing under the pressure of nuclear bombing, so it was neat and tidy without any mess.

"What the heck, Zhuge, morning, haaaam. Gaaaah. Oh my, it's so early in the morning, really."

Qing yawned and made a sound like an old man.

But, as they said, anything a beauty does was forgiven, so any man would gladly accepted it and even praised it as a surprising easygoingness.

"Sister, why don't you try exercising a bit for the first time in a while? You need to let your muscles loose once in a while to avoid becoming lazy, don't you?"

"Huh."

\textit{Muscles aren't like internal combustion engines, so do they need to be stepped on occasionally to get rid of the dirt?}

\textit{If you suddenly act wild, won't you just cramped?}

But Qing doesn't know anything about exercise science, and maybe that's not the case here in Zhongyuan.

In this world, even the special organs of humans, the circulatory channels of the cosmic mystical energy, the Qi and blood, become blocked and hardened if you do not regularly exercise.

Qing was a very open-minded person.

If one were to suddenly find themselves in a pseudo-martial arts world resembling the ancient primitive Zhongyuan, wouldn't anyone's heart open?

"What are you talking about so early in the morning?"

"Sister, that's what I mean-"

"Wait a minute. There must be a very good reason. Otherwise, daring to disturb an elder's morning sleep would be an incomparable act of disrespect."

Surprisingly, given Cheong's status, it was a well-known fact, with not a single hint of falsehood.

Zhuge Lixian explained to her.

The first entrance exam, as its name suggests, was only the first.

First stage meant that at least there's a second stage.

The second entrance exam began today.

This test required you to chose one of three skills: cutting wood with a sword, cutting stone with a sword, or cutting iron with a sword, and proved your mastery of the martial arts you have learned so far.

However, trees wouldn't suddenly grew in the testing area, or rocks and iron would suddenly sprout up, so wouldn't everything have to be carried and moved by people?

"Oh, so Zhuge wasn't just weighlifting back then."

"Weighlifting? The meaning is quite clear. Indeed, you've always used such unique, yet intuitive, expressions."

When Qing first arrived at the temporary headquarters of the academy, Zhuge Ihyeon was holding a huge stone slab.

Since Zhuge Lixian boasted of an outstanding physique, she thought she was just training his external skills, but it turns out he was transporting materials to be used in the second test.

Of course, nobodye would never ask the heir of the Zhuge Family to do such a menial job, so he must have volunteered for the purpose of training his external skills.

"Well, if that's the case, then whoever that could help should help."

Qing readily agreed.

After all, they're all part of the same Wulin Alliance, so it was understandable why some people sleep early while others stay up until dawn, struggling to move things.

If she didn't know, she wouldn't know, but now she knew.

As the realm of your martial arts increased, the amount of sleep required also decreased. She didn't know the principle, but she thought it's somehow caused by the great mystery of Qi.

So, wouldn't Qing, a master of Unrestrained Realm, be one of the people in the admissions office of the Yizheng Martial Study Hall who needed the least amount of sleep?

For Qing, sleep was a hobby, not a necessity.

Following Zhuge Lixian, she passed through the guesthouse gate and entered the main building. It was a complete mess, as if there's a construction. Everyone was struggling to move the stone slabs, tying it to the iron pillar, and pushing and pulling them on carts.

In the meantime, there was a giant, autonomously moving stone slab…no, it was just Peng Chaolei carrying a stone slab on her back.

Peng Chaolei greeted Qing with a smile.

"Oh, Qing'er, did you come out to help? Yeah, what's the point of lying around all morning and slumping around? Stretching your muscles and loosening them up will make you feel refreshed all day long, and it'll make you feel good."

That's exactly what Zhuge Lixian said.

\textit{What the heck? Is this really common sense in Zhongyuan?}

While she was wondering, she stopped by the materials warehouse and there was something that was bright and dazzling from the morning.

It was the dazzling teeth of Withe Tusk Sword Wu Zhangyue.

"Hmm? Instructor Ximen? What are you doing this early in the morning? Why don't you get some more rest?"

"I came to help because I heard there was work to be done."

"Haha, you're truly unusual for young people these days. If my son were even half diligent as Instructor Ximen, no, even half as half as much, I'd be carrying him on my back."

Wu Zhangyue had been very likable ever since she had saved his reputation in the incident where Qing had destroyed the back of the dancing guy.

"I appreciate your kind intention, but please get a little more rest and let the workers handle this kind of work. For martial artists like us, we're just helping out while also training for external skills. Everyone else is getting paid for their work, so there's no need to feel uncomfortable."

"Hey, shouldn't I try my best too?"

Qing raised her arms and flexed them.

Even so, the puffy sleeves flowed down, revealing only the deadly, beautiful, snow-white arms of a so-called 'Vajra-indestructible' or, if you must a 'Vajra-indestructible So-so Witch'.

"Oh, Great Expert. Sister's strength are truly a legend among external skills practiotioners."

"Hmm?"

"Ah, Great Expert. Xian'er is right. Qing-ah is a real talented with external strength, isn't she? Even I'm embarrassed to use nicknames in front of Qing'er. Qing-ah should be the one called Female Xiang Ji, not me."

Peng Chaolei chimed in.

Wu Zhangyue's gaze turned to Qing's slender wrist. It was so fragile that it looked like it would snap if he gently twisted it.

"Okay, can I move this? If you're tired, you can rest. Bye."

Peng Chaolei nodded happily.

Zhuge Lixian's eyes sparkled.

Wu Zhangyue's mouth dropped open.

Isn't it the sight of someone lifting a stone monument lightly as if they were carrying a tray?

Since exerting strength naturally produces a characteristically strong appearance, it was common in external skills training to roughly gauge the strength exerted simply by looking at the height of their shoulders.

Ini other words, not much effort was being put into it!

Furthermore, you're going to bring that forward?

What the hell was with that grip strength?

If Wu Zhangyue was surprised like this, how surprised must the Wulin Alliance workers be?

When Qing passed, the carts pulled by the laborers all stopped, and everyone rubbed their eyes, wondering if there was something wrong with their sight.

Are they seeing things after wexerting themshelves since dawn?

However, the buffer between the stele and Heavenly Blossom Sword was a truly magnificent sight, an unprecedented items that made the workers envious to the stone slab, a sight that one could not take their eyes off.

"Oh, Monk Weifeng is here too."

"Cough."

Thud!

The bald man, whose face was hard to see, finally greeted her, but then he stumbled and fell, crushing him under the stone slab.

"Huh? Are you okay?"

"It's okay, it's okay. Namu Amitabha Buddha."

A clear answer came back from under the tombstone.

After all, Weifeng was the true owner of the Diamond Indestructible Divine Art, the human Diamond itself who remained unscathed even after being beaten so much by Qing.

After a few moments, the tombstone slowly rose.

And as he was looking up at Qing , -Mara, no, Amitabha- he hopelessly looked for Amitabha and slowly lay down again.

"Are you really okay?"

"Hmm, you go first."

\textit{This guy was also a bit, no, very strange.}

\textit{But contrary to the first impressions, would someone asked a Shaolin monk to carry stone slabs?}

\textit{The fact that he's here means that he had volunteered to help, so I guess she's not a bad person after all.}

Qing walks along with a steady step, carrying a stone slabs.

This too was a mysterious sight, how on earth could she saw what was ahead and stride forward so briskly?

It was a figure that looks like a rock with legs that towers high above the head and was as tall as a person.

Well, Qing didn't see the world only with her eyes.

As she came out holding the stone slab, Qing's Awakening Sense spatial perception sensed a human figure with a unique shape.

\textit{Oh, who does this look like?}

"Sima-lang?"

"Heavenly Blossom Sword? No, what kind of power is this? This is Sima-lang's defeat. No, if this is the official match, the winner will be…"

Qing reflected a little.

\textit{There are so many people working from dawn, but I just sleeping around.}

\textit{Isn that right? Did you start working today? Anyway.}

"Ahem, Heavenly Blossom Sword. If you think you've defeated Sima Lang with this, you're making a grave mistake. Our fight begins now—"

"You've been working since dawn? You must be tired."

"Hehehe, hehe! That's the fate of geniuses like us, people who can see through one thing and see through all."

\textit{I wonder how many 'fate of geniuses' still left, and seeing them come out so seamlessly, I have a reasonable suspicion that she's always pondering them.}

Of course, Qing's suspicions were not suspicions but very clear facts, but Qing did not have the ability to read people's minds.

"What can we do? If it weren't for Sima-lang, the entire work of the Wulin Alliance would be paralyzed. That's precisely why we can't entrust Wulin Alliance to those incompetent, ordinary people who are inherently negligent."

The warriors of the Wulin Alliance had expressions on their faces as if they have seen a dirty sight since morning.

But that's not something that only happened for a day or two.

Everyone knew how Sima Chunfeng was both a very honest and unpleasant person.

The hard work that started at dawn like that ended early as the space under the evaluation hall's viewing area filled with materials.

\textit{Well, I don't know if it's refreshing.}

\textit{I would say that I definitely eat more breakfast after working out in the morning.}

The second test wasn't that time-consuming, so it went by much faster than the first one.

The testing site was equipped with bamboo stands, stone slabs, iron plates, a stone stele the size of a person, an iron pole, and so on.

Applicants were asked to chose at least one to ten pieces of bamboo, or one of the following: a stone slab, an iron slab, a stone stele, or an iron pole. They were asked to demonstrate the power of the martial arts they have learned by cutting, striking, or stabbing them.

But more importantly, if you took on the challenge, you must succeed.

To begin with, the admission criterias for Yizeng Study Martial Hall were not based on ability.

This came from the very beginning when recruiting applicants for tYizeng Study Martial Hall, so didn't it say that they would recruit people with the right spirit and determination regardless of their abilities?

So, the main evaluation criteria for the exam were how accurately they would know their own abilities and how accurately they could demonstrate what they had learned.

But how could young people, who were at most in their mid-twenties and even young boys, do that?

'This time I'll show you something', so it was bound to be a fantastic martial arts demonstration.
