\chapter{Yizheng Martial Study Hall, Opened (6)}

As you climb the gentle slopes of Mount Baiyun, you will be amazed by its gentle and beautiful scenery.

Although Henan was a relatively hot area in Zhongyuan because it was inland, entering the forest of Mount Baiyun made it surprisingly cool and gives you an incredibly refreshing feeling.

Even when the seasonal wind blows through the valley and onto the forest path, it was so cool that it was almost chilly.

The hearts of those who have passed the Yizheng Hall examination were greatly lifted, and a good feeling somehow fills my heart and makes my chest feel grand.

The youngest member of Qinghai Virtuous Six, Ma Dazhe, was also like that.

"Oh, I wonder why the school was open this summer. Brother Yang, isn't it really cool?"

"Yeah. It feels good."

So, at first.

I climbed the mountain early after breakfast, and the hike felt good for an hour, or at most two hours, so no matter how much I walked, the endless uphill road showed no signs of ending.

After about two hours, the sun began to rise and it got hot. The hike continued endlessly, and I was bitten by the fierce mosquitoes.

Around noon, the unmanned people staying in the dormitory took a breather while eating the glutinous rice balls prepared by Maeng, who had brought lunch with him.

The fatigue from walking all the way was coming back to me and I am starting to feel really tired.

"Brother Ma, are you okay? Hand over your luggage here."

"I don't get tired of this much."

"Who cares about you? If you keep lingering, you'll arrive late. I'm just frustrated."

Ma Dazhe blushed and banged his head at the words that were thoughtful and not embarrassing.

"Whew, I may be shameless, but I owe you a favor, Brother Yang."

"I'll put it on hold, so pay me back later."

And then again, just the back.

The Mount Baiyun range, with its gentle slopes below and rugged terrain above, was starting to reveal its true colors from around here.

The gentle mountain path becomes steeper and pulls at your ankles, torturing your calves.

From the perspective of entering the academy, I can't even rest in the middle of the course for fear of being late.

At the third-rate level, sweat starts pouring down like rain, and even at the second-rate level, you start to feel out of breath and a sense of tension sets in, thinking, 'Ah, this wasn't easy.'

"Whew, it's rougher than I thought. But."

Ma Dazhe looks to one side.

At the end of spring, amidst the completely lush green foliage, a woman wrapped up in thick fur, boots, and handcuffs (gloves) stands.

Qing said, "It's the firework girl Che Yaohong."

Even though he was wearing midwinter clothes that make you feel hot just by looking at him, he does not break a single sweat, and although he walks with his characteristically weak steps, there was no sign of fatigue at all.

"I guess she doen't feel the heat. Even if you don't, it's also because your inaction was so degrading."

Of course, if you were a first-class driver, you will be enjoying the hike from the beginning and just enjoying it to the fullest.

In the first place, the age limit for the martial arts academy was set at 30 years old. If you were a young man who had achieved first-class status, your goal would be to enter the martial arts world of the Jeongpa faction. Mathematics wasn't that far off.

Climbing up and up that endless, endless uphill road, the mountain path becoming increasingly rugged.

Finally, the sun began to set, and that damned State Councilor was nowhere to be seen.

Maybe I took the wrong road. The way up was a single road with no other way, and since it was a single road, that couldn't be possible.

But why can't I even see the school building's nose?

At a time when my heart was filled with such anxiety.

As you pass over the cliff that rises beautifully on one side of the valley road, a huge gate appears as if it were a lie.

Yizheng Martial Study Hall!

"Ahhh……!" "I'm here! The Yizheng Hall!" "Ohhh!"

The spirit of the successful candidates soars, and loud shouts erupt from all over.

The day's hardships and anxieties melt away, and a grand sense of accomplishment fills the void.

I'm here! Finally, the Yizheng Martial Study Hall!

It was a moment when a thrilling feeling wells up.

And so, as if welcoming them, the shoulders of the successful candidates who pass through the wide-open main gate stand tall and proud, and they enter with a confident expression full of ambition.

Because it was designed that way from the beginning.

Qing was also perfectly hidden behind the cliff, but when he saw the royal tomb of the Jeongmu Academy suddenly revealed, he thought, "Wow, this was really well built. There was no place like this."

And as a carpenter, it was also a very impressive piece of architecture.

Saying they had worked hard, they ate a small but plentiful dinner, and the women took a quick bath in the bathhouse set up by a wooden fence upstream, while the men took a quick bath and cleaned their clothes in the valley that stretched out below the side gate.

And after taking a brief breather and counting the number of students, the entrance ceremony was held in the pitch-black night when the sun had completely set.

As they wait in a neat line at the main stage, Yu Shan-ye, the director of Yizheng Martial Study Hall, came up to the podium in front.

"Thank you all for your hard work getting here. No-"

After a brief pause, Yu Shan-ye Ye shouts in a thunderous voice.

"Thank you for coming this far! From now on, you are all officials of the Yizheng Martial Study Hall, and I will be your director. Do you need any more explanation?!"

"No!" "No!" "No!"

Rather, it was the officials who answered loudly.

At that, Yu Shan-ye smiles.

"I am your leader! And being responsible for your means that you are all under the responsibility of Wulin Alliance! And the reason Wulin Alliance was responsible for you was because you are warriors with the righteous will to establish justice in the world of martial arts! Isn't that right!?"

"That's right!" "Okay!" "Yes!" "That's right, ok!!"

The answer resounded loudly, followed by a roar of joy, a mighty roar that woke the night in the mountains.

Qingdo, who was waiting for the introduction in the waiting area behind the stage, couldn't hold back his exclamation, "Hmm, this was a total mess."

What's the big deal, even the answers aren't unified?

And who told you to shout?

Of course, that's natural, since a series of formalities called rehearsals were not carried out.

After a while, the cheering subsides and Yu Shan-ye's voice rings out again.

"Yes, before we proceed with the ceremony, I want to tell you just three things.:

What were the three things that the higher-ups have?

Whether it's a congratulatory speech, an opening speech, or anything else, when you go up on stage, don't you always present three things?

I thought it was only in my hometown, but I didn't know that the three histories were this old.

Well, in the Four Books, Confucius, Mencius, and even Sima Qian, they always mentioned three things. Well, if you think about it, in the Western Regions, they also say it's the Trinity. Maybe humanity has some kind of instinctive preference for three things.

"One. Agreement comes from the heart. The honor of one's military achievements, the honor of one's birth, or the wealth of one's property were of no importance…"

"Sima Qian said in his Shiji…"

"Confucius said to Zilu, 'Keep on… …"

"If you look at the past track record and see the traces… …"

Then Peng Chaolei blurted out a word.

"Uncle Yu still talk a lot."

"Oing? Is it okay to say that?"

When Qing-i glanced at Yu-wook-ah's, the Taesan Sect Daoist smiled bitterly.

"That's why we must always invite the leader to Wulin Alliance events. If the leader is absent, wouldn't Master Yu step forward?"

It didn't sound like a joke to Qing.

Because 'one' hasn't ended yet.

After doing this much for one, were you still planning on doing two and three? Seriously…?

For some reason, Master Yuuk-ah told us not to go up on stage and to wait behind the stage until the introduction.

He insisted on bringing a chair there.

If I had been on stage, shouldn't I have just pretended to listen without moving?

"And the second was loyalty. As the Buddhists say, even a brush of clothes was a connection, so you who have gathered as a class and studied together…"

Yu Shan-ye's words continue on and on.

"The third was diligence. Diligence means diligence. Jeong refers to rice that has been washed clean and free of dirt, and Jin was the character for progress…"

"Also, to proceed correctly, here, correctness means… …"

"And Jeongjin, this was Jeong, the Jeong that you all know well, the example of Nanggungjichu, the image of standing out from the crowd was Jeongjin… …"

The third time, there were three more diligences.

Even in Omok, three threes were prohibited, so I wonder if this was crossing the line even for the manager.

"I think it's finally coming to an end."

"No way." "No."

The two instructors answered at the same time, with the same expression and bitter smile.

"Huh? What else is left?"

"Listen." "Listen."

"Well, that's all I have to say. Ahem, I guess I've said too much. But it wouldn't hurt to keep this in mind. Don't think of it as just some old man's nagging, and think about it seriously for a moment. Got it?"

"Yes!" "Okay!" "I understand!" "Oh!!" Then the replies poured out enthusiastically.

Well, it's admirable that you've endured this long.

however?

"And finally, I have one last request: Receivers, protect yourselves. In the first place, martial arts…"

It was a surprise attack that came out of nowhere.

If you're going to discuss reception there and start talking about martial arts, were you planning to stay up all night tonight?

Maybe it's some kind of newbie hazing.

The officials must already be tired from climbing the mountain, but holding the event in the middle of the night really sets the mood for the event.

The last words were truly necessary: never overdo it while training in the academy, get plenty of rest when you need to, force yourself to eat even when you have no appetite, and don't do anything dangerous.

No matter how desperate you were for knowledge and how thirsty you were for learning, what good was it if your body was damaged?

I think that if you want to protect yourself now, you have to get up right now and break free from the shackles of endless preaching.

It was a sermon that seemed like it would go on forever, but what in the world could be eternal?

"Well, I've gotten too long. That's all I want to say."

Again the shout, the shout of freedom, the shout of liberation.

Can you hear the people's cries?

-Okay, then I will introduce you to the instructors who will teach you martial arts.

Three people stand up from their seats.

Three people climb onto the stage.

The officials gulped and tensed.

How could it not be hard to listen to a long lecture while standing upright, with a tired body and a sleepy mind?

Even if you doze off or yawn and get caught, wouldn't that be a huge embarrassment even before the entrance ceremony?

So, the officials can't help but be nervous.

Surely, surely, he won't come up again and say something, I thought.

But that tension was short-lived.

The officials' eyes widen as the stage suddenly lights up brightly.

It's not that it's actually bright, but it's just that a brightly bright beauty has come up on stage.

It was the face of the most beautiful woman in the world, a subject of much rumour.

That too, with her makeup done and caught by Pang Chaolei, asking if she was just going to the event, she was in an aggressive beauty stance with the best fighting power.

My tired body and mind feel instantly healed and energized.

Someone let out a "Wow!" without realizing it, and a warm welcome poured in for the instructors climbing the mountain.

That was when.

"Quiet!"

It was a huge force that had properly raised the internal energy of the rich and swindler Ximen Qing.

Moreover, Qing's voice was beautiful, a beautiful voice that penetrated all obstacles and entered the ears, so I could not help but keep my mouth shut in confusion at her harsh yet beautiful strange cry.

And so, as soon as the commotion died down, the peerless man, with a large, muscular woman on the left and a large, muscular Taoist priest on the right as his escorts, finally opened his lips.

At that moment, when everyone was focused and looking at the scene, a shout of laughter rang out.

"This serg-, no, this instructor, is very disappointed!"