\chapter{Yizheng Martial Study Hall, Opened (3)}

The third entrance exam was a stage to measure the level of the Lightness method.

It was a makeshift obstacle course made of stakes to set footholds, ropes to make a path, a superstructure with a blocked ceiling that required hanging from ropes, and walls made of stone monuments.

\textit{As a laborer, or rather, a leading laborer and carpenter, I participated in its construction, but, um, what should I say? It looks very familiar.}

\textit{Guerilla training, yeah, it feel like the conscription's guerrilla training.}

There were also several difficulty levels prepared.

The easiest route to cross the shortest distance was one that can be passed with just a basic sense of balance and enough muscle strength to support your body weight.

However, the most circuitous route was designed to require a fairly high level of Footwork Technique.

Although Yizheng Martial Study Hall had not been opened for a while, it was a design that has been supplemented over a long period of history.

They say that the further you go, the more points you get, so everyone chooses the longest route possible.

(Of course, the points added and deducted don't mean much)

So, how much fun would it be for the crowd to watch the applicants desperately flying around?

At this point, it's not even an entrance exam, but rather a martial arts event where martial artists gather to show off their skills.

It's like those quack who sell suspicious medicines, if you set up an acrobat show in front of it, the medicine would sell like hotcakes.

And in fact, it was in the process of doing so.

The only difference was that they were selling fame, not medicine.

Look, this was what the Wulin Alliance does.

Aren't these outstanding martial artists desperate to seek the teachings of Yizheng Martial Study Academy?

Do you see the difference in the level of our academy, the rank of our Orthodox faction, and the power?

You could say it was an outrageous act that turned the applicants into medicine peddlers and fake shamans.

But Wulin Alliance was not a philanthropist organization, and they can't even made profit by providing food and shelter for martial arts.

Above all, if you're not interested, just leave.

But the test takers struggling to keep their balance, jumping around, and jumping here and there.

Well, most of them were just Third-Class or Second-Class people.

This shows how great an opportunity and how great a benefit it is provided by the academy.

In that sense, if someone like Cai Shengxia or Sword Jade-lady has already achieved a realm above First-Class, there should be no need for them to desperately cling to Yizheng Martial Study Hall.

"……So, those who stand out among them each have their own purpose, right?"

This was Sima Chunfeng's explanation.

The long entrance exam, which continued through the first, second, and third stages, was intended to spread awareness of the events of the Wulin Alliance, but it was also intended to catch as many impure people as possible.

"Isn't Young Expert Cai easy to understand? He simply seeks fame, isn't it? Is it the limitations of these ordinary people? Innate inferiority complex? Well, if they have abilities, fame naturally follows. However, the common people's desire for fame is the driving force that allows them to imitate, even if only a little, the immortals who, like us, have left their names in history."

"When you first saw Azure Dragon Dancer, didn't you say he have a good talent? Did he secretly fall into the ranks of ordinary people?"

"Look, when did this Sima-lang said that? Framing me would be problematic."

While they were talking about such trivial things, the next person to come up was none other than the nobleman of Sichuan, Wan Talu.

\textit{Isn't he going to be eliminated anyway?}

\textit{His Evil Karma isn't quite three digits, but his character is a bit lacking.}

\textit{If he handed out a business card saying that he graduated from Yizheng Martial Study Hall, it is obvious that he'd be getting a lot of flak everywhere.}

But.

"Oh!" "It's fast, it's fast!"

Unlike the disgrace he displayed in this second test, he gritted his teeth and ran over the obstacles. 

\textit{What the heck, pretty good?}

He jumped over the stakes arranged in the shape of a letter "Gal-ji" three at a time and stepped forward precisely, then began to quickly overcome the obstacles placed there.

\textit{But, um, that. If you keep going like that.}

\textit{That's too fast.}

Lightness was not just about running with all your might, but it was also about being able to perceive your surroundings and adjust your speed according to the situation.

He was gritting his teeth and his eyes were filled with venom, as if he was rushing to make up for the disgrace he showed during the second test.

As expected, he jumped up and stretched his arms high as if trying to jump over the temporary fence structure in one go.

It was a leap that was just one cun\footnote{Chinese unit of length. 1 chun = 32 mm} short.

Bang! The palm that should have been hanging on the top only hits the poor fence hard.

And that was the moment.

"Oh?" "Oh!" "Huh."

To their surprise, Wan Talu's body rose again by about one cun and grabbed the edge of the barrier.

It was an amazing feat created by the elasticity of the body and the two legs that were raised in the air in an instant.

"Oh, did you just see that?"

"That's…"

Sima Chunfeng's expression was serious.

Her already fierce expression became even more fierce.

"What?"

"It definitely looked like Flying Clouds Chasing Shadows."

It was the name of one of Dianchang Sect's martial art.

But if a disciple of Dianchang Sect had deliberately hidden his identity and applied to Yizheng Martial Study Hall, then it would have been a serious problem.

Because it means that the martial arts have been leaked.

"Then what should we do?"

"He's a petty person who should have been eliminated, but in this case, there's nothing we can do. For now, we have no choice but to let him pass and then find out his origins."

Qing looked at Wan Talu.

As he reached the finish line, he was met with the admiration and praise of the crowd, trying to appear calm but unable to control the corners of his mouth as he smiled.

What he does was exactly the same as Azure Dragon Dancer.

For that reason, the nobleman of Sacheon Castle passed.

You could call it a pass, but it's probably closer to arrest or detention.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The exam schedule for Yizheng Martial Study Hall was now closed!

It was a very satisfying sight for the tourists.

In Zhongyuan, where there's always a shortage of things to see and do, this was an exceptionally splendid spectacle. And what if there were any famous warriors among the contestants?

At that time, they would have something to brag about for the rest of their life, saying that they were the one who witnessed someone's rise to Jianghu.

The time leading up to the announcement of successful applicants was when the military in the academy became really busy, and for the rest of the people, it was a quiet time with nothing to do.

And so, the moment that Murong Juhee had been waiting for finally came.

"Excuse me, Young Lady Ximen? That martial arts…"

"Oh, right. I said I'd help. What was it called? Douxingzhuan? Is that right?"

\textit{Is it perhaps a type of yin-gong? Just hearing the name, it sounds like a martial art that would make a sound in the upper chamber.}

"It's not Douxingzhuan, it's Douzhuan Xingyi\footnote{斗转星移; Shifting Stars Transposition}……"

Dou means a mal of grain, a large ladle of wine, or the Big Dipper.

In other words, the term 'Douzhuan Xingyi' refers to the phenomenon in which the Big Dipper rotates and moves all the stars, and was originally a character used by astronomers to record the movement of stars while observing the sky.

And it was also the strongest counterattack technique that could return the full force of the enemy's attack, a family secret that only the direct descendants of the Murong family could master.

"Oh, isn't it the pinnacle of grafting? Am I right?"

Grafting\footnote{移花接木; Yihuajiemu; lit. 'move flower connect tree'} was the art of using the enemy's power, and in fact, if you become a master, you will naturally be able to use it to that extent.

"Yes. However, it was a bit difficult."

"Well, then shall we go to the training ground?"

"That, without holding back! Hard! That, that's because if you don't, I won't be able to cultivate, right?"

"Huh. Then Young Lady Murong will be torn in half. Is it possible for her to become Young Lady Mu and Young Lady Rong?"

"Uh, uh, like when you taught that guy named Yang Qi. If you fail at a skill, it'll sting, sting, sting. That's why I'll be able to train, too. There's no other meaning to it, but that's why, that's why."

The way Murong Zhuji spoke like that was somehow awkward and her voice was trembling.

Qing was impressed.

\textit{Oh my gosh, how wonderful this girl can be.}

\textit{It seems like only yesterday that she was acting like a wreck, hurt by a bad experience, but now she have a strong attitude to overcome even those painful memories.}

\textit{If you think about it, Murong Zhuji, who began to follow the unique family tradition of the Murong family, is a figure who symbolizes the Half-Sword Double-Saber Association itself.}

(You may not want to become a symbol of something shady like the Half-Sword Double-Saber Association.)

\textit{Our members should also follow Young Lady Murong's example and be this enthusiastic, um, enthusiastic?}

\textit{If you think about it, everyone was so enthusiastic that they naturally start training, even if you exclude Sword Friend, who was overly enthusiastic, and Gunyeong, who was a serious energy addict.}

\textit{Among the members, the only one who hangs around and plays around is, um, Lan-ah?}

\textit{Sometimes she pretended to throw hidden weapon, but strictly speaking, it's not training, it's more of a hobby.}

\textit{Even Changming'er was so enthusiastic that Sword Friend praised her.}

\textit{It seems like enthusiasm are overflowing.}

\textit{Thinking about it that way, I think Young Lady Murong was a little less special.}

"Okay, shall we take a look then?"

"Yes, Young Lady! Please take care of me!"

Qing first used the Ximen Surin-style Divine Maiden Sword First Movement, Heavenly Maiden Great Man.

\textit{I don't know the level of Young Lady Murong, I couldn't just suddenly use maximum power.}

The secret of nuclear weapons was to generate maximum power without harming the body, not to break the head of a person while killing them.

A powerful blow containing Ximen Surin's magnificent spirit rushes towards Murong Zhuji.

In an instant, Murong Zhuji's left sword slanted and swung down with its steep blade, and the moment it touched the center of Qing's wooden sword, the wooden sword in his right hand clung to it and changed direction.

\textit{Oh, like this.}

Qing quickly twisted her body and dragged her feet out to avoid the wooden sword aimed at her thigh.

"Hmm. Certainly. It won't be possible to practice slowly. The faster and heavier the enemy, the more difficult it will be."

"Yes, yes. That's right. If you do it slowly, you won't be able to practice…"

Murong Zhuji was acting like a small animal, shaking and trembling like a baby animal, and was trying to catch the eye.

\textit{Her face looks a bit red.}

\textit{Was that move just now that hard?}

\textit{How can you use this in real life?}

But that's why you asked for a duel.

For someone who wants to improve, the current state of affairs was no problem.

The swordsmanship of Qing gradually becomes more fierce.

However, Murong Zhuji was also a master swordsman who has reached the pinnacle of swordsmanship, but by the standards of Qing, she was considered a weak person, so shouldn't she train twice as hard?

Boom boom, Qing swordsmanship was slowly gaining its strength.

Murong Zhuji desperately returned the blow with unprecedented concentration. Because it wasn't yet the time.

Then, Qing swordsmanship becomes more and more strict.

The tip of the sword fluttered, mixing the subtlety of illusion and change, sometimes stretching and mixing with the illusion, and gradually increasing the angle at which it bent and curved, launching an irregular attack.

Despite her somewhat sly nature, Murong Zhuji has no intention of deliberately revealing her weaknesses.

\textit{Not only would it be rude to Young Lady Ximen, who sincerely helps, but I would ultimately be unable to cope with attacks that exceed my limits. Only then can I truly feel the sting, the sting—}

Puck!

In that moment, Murong Zhuji's mind went blank.

The legs naturally gave out and the body collapsed.

And only then did Murong Zhuji realized.

Pain was just pain, not stinging.

\textit{Oh, it hurts… … ? It hurts so much… … ?}

She realized it too late. Life was a battle.

"Uh, Young Lady?"

"Ah, are you coming to your senses?"

Actually, Qing didn't hit her that hard.

And Ximen Surin's educational policy was that if you know you're in pain, you'll fight back even more desperately, which was a very obvious principle.

The more you suffer, the more you mature. Pain was what gives you answers, and frustration was what makes you a warrior.

"Uh, uhm."

"Honestly, I think I underestimated Young Lady Murong a bit. I saw her as too weak. Well, you're a low-level warrior, but if you don't like being low-level warriors, you should at least try to become a mid-level warrior. Okay, let's do it again."

"…Yes, yes. Please."

Murong Zhuji couldn't bring herself to say that she hadn't wished for this.

The expression for this was 'self-inflicted disaster', meaning that one brings disaster upon oneself, and 'self-flagellation'. meaninng being overconfident in one's own pain threshold.

However, apart from that, the most desperate training period in Murong Juhee's life continued.

Why, they say even a whale can dance.\footnote{The title of self-motivation book 'Whale Done' was somehat wrongly translated to 'Praise makes even a whale dance' in South Korean publication, and it's somehow believed was a 'traditional' idiom.}

This was the moment when Ximen Surin's educational method has once again achieved a great victory.