\chapter{Yizheng Martial Study Hall, Opened (4)}

From lunchtime, the front gate of the Admissions Office of Yizheng Martial Study Hall was bustling with countless people.

Because it was the time when the successful candidates were announced.

Then, at noon, the hour when shadows were at their shortest, the closed gate begins to open with a creaking sound.

And a middle-aged warrior strides forward with a confident gait!

This was the Dean of Yizheng Martial Study Hall, Sword-Dominating Dagger Yu Shan-ye.

The dagger-wielding warriors who had climbed onto the platform looked around in all directions and then let out a roar of great power filled with Inner Qi.

"I, the Dean, am truly moved. It was thanks to the sincerity of all of you who aspire to enter Yizheng Martial Study Hall! Therefore, I, Yu Shan-ye, would like to express my gratitude first, not as a senior, but as someone who dreams of becoming a member of the faculty!"

-Wow!!!!!

A cheer erupts.

After a while, when the cheering died down, Yu Shan-ye raised his voice again.

"The youth you cheered for, why did these young men seek study at Yizheng Martial Study Halls? To uphold the principles of the world, to inherit the spirit of the chivalrous warriors, and to practice justice! You have already witnessed their determination. Their fervor for upholding the principles of the world was so fervent that it melts iron and leaves more to be desired. Their determination to practice chivalry was so lofty that even the mountains of the earth will bow their heads in shame!"

-Wow!!

"Therefore, as a senior member of the Orthodox Wulin, and as a representative who must guide the will of the trainees on the right path, I hereby promise to fulfill my grave responsibility! Therefore (omitted)… Congratulations on your trainees inauguration!"

-Wow!!!!!!

"But this is just the beginning-"

-Wow……

The tail end of spring. Now, under the scorching sun, everyone's backs were soaking wet, and only then does Yu Shan-ye's magnificent eloquence finally, finally, finally, get to the point.

"I would love to embrace all who have applied to learn and walk the path of righteousness together, but my preparations were limited, and I cannot embrace everyone. Therefore, those who did not pass should not be considered to have any particular problem; they should simply consider it bad luck."

Hueup, and then Yu Shan-ye took a deep breath.

"But!!"

Under the scorching sun, they gradually grew tired of the thunderous sound and listened intently.

"I would like to inform you here that the opening of … has been decided for next year as well!"

They decided to do it for one more year!

Especially, those who were eliminated this time will be given a lot of extra points next year, so don't be too disappointed.

Then, a loud cheer of "Wow!!!" swept through the hall again.

The spectators were excited that such a spectacle would be held again next year, and the test takers who were nervous before the announcement were also greatly relieved that it would be held again next year.

Then, the staff of the Wulin Alliance walked out and quickly put up posters on the wall.

It was a list of successful applicants, with countless names engraved on it.

Yang Qi scanned the posters on the wall, his face hardened with tension.

His seniors at Qinghai Virtuous Six said that there was no way he wouldn't pass, and that he would definitely pass.

But there were no absolutes in this world, so Yang Qi's heart, which was searching for his name, pounded violently.

And then-

"Congratulations, youngest!" "Didn't I tell you not to worry!" "You rascal, you can't pretend not to know your brothers now you're going to become an expert?"

Right next to him, Ma Dazhe was being pressed, beaten, and shaken by the rough congratulations of his brothers.

Yang Qi also took his eyes off the poster and was about to congratulate his friend.

The youngest of Qinghai Virtuous Six, Ma Dazhe, pointed his finger at one side while looking at him.

"Brother Yang! Brother Yang! Look over there!"

\begin{quote}
	… …

Yanchang person, Xiao Yindiao

Yanchang person, Zhang Feihu

Zhaoqing person, Yang Qi

… …

\end{quote}

"ah."

Yang Qi opened his mouth blankly.

\textit{What should I say, I have no thoughts, to be exact, I can't think of anything.}

Then bang!

Yang Qi finally came to his senses at the sharp hand patting his back.

"Haha, what a fine day. It's a shame to miss out on a drink on a day like this. It's a special occasion for my youngest brother, so I'll have to empty my pockets today. Ah, this is kind of bribe. Please take good care of our youngest brother, Young Expert Yang."

It was Qinghai Virtuous Six oldest brother, Chogaksan.

So, six people plus one more left the place with bright faces, chatting about drinking from noon until noon tomorrow.

In the remaining space, there was a young man who does not look at the poster and only glared at others as if he was going to kill them.

Following that gaze, another young man appeared, his fists clenched in front of his shoulders, expressing his joy.

\textit{Now that I've passed, I can say that changing my surname was worth it. I'm now completely free from that stinking corner of the house.}

After Zhang Feihu was enjoying such joy, he turned his head at the sharp gaze and met the angry face of Xiao Yindiao who was glaring at him.

Zhang Feihu was startled and wiped his smile, then pointed to the poster with an awkward face, took the announcement slip, and slowly backed away.

After his family's enemy completely ran away, Xiao Yindiao looked at the poster and soon found his name in the spot he had pointed out.

\textit{I guess they put it that way because it's the same hometown. I'm happy, but I can't be completely happy.}

Xiao Yindiao sighed deeply and turned to wade into the crowd. No, he tried to wade in, but bang.

He bumped shoulders with someone.

Xiao Yindiao apologized first.

"Oh, I'm sorry."

"Sorry? Ha, now that shit is starting to feel like a big shot. I'm speechless."

He was careless and the other person was careless, so it's not anyone's fault.

Xiao Yindiao was fuming, but he wasn't so senseless as to cause a commotion at a time like this.

\textit{I could endure even seeing my enemy, so why wouldn't I be able to endure seeing such a petty person?}

Moreover, Xiao Yindiao knew that this little guy was a fairly strong warrior, and that person was Wan Talur, who had sold his face quite a bit in the exam.

"Ha, you should know how lucky you are. If only it weren't for this moment, it wouldn't end just like that."

Wan Talu growls, spits, and approaches the poster.

\begin{quote}
	… …

Foshan person, Zhang San

Jianyang person, Wan Talu

… …
\end{quote}

"Huh."

Wan Talu's response was brief.

Well, that was already expected.

If the judges of the Wulin Alliance weren't so savage, how could they turn down a young master who had achieved such great things?

He was just checking just in case, because he was Wan Talu who never doubted his own passing in the first place.

"Senior, why isn't this junior's name listed? Is there a mistake? I'm sure I did well on all exams, but…"

A candidate holding a poster and complaining catched Wan Talu's eye.

\textit{What are you, Senior? Are you a lowly swordsman who does odd jobs under the largest group of thugs in the world, a privately organized group called Wulin Alliance?}

\textit{To the lowly ones, if you say you're a martial artist of Wulin Alliance, they might seem like great men, but they're just thieves who don't know the law of the land.}

\textit{But, that's just how it was for lowly people.}

Wan Talu chuckled and left.

However, the warriors of the Wulin Alliance had to guard the poster against any damage, so they could not leave their positions.

So the warrior of the Wulin Alliance politely scolded the polite observer who has caught him.

"Well, it's unfortunate, but if admission was determined solely by merit, it goes against the academy's policy of upholding justice. We're short on space because we're selecting individuals from various backgrounds. So, you'll definitely pass next year. Just persevere for one more year and continue your studies."

"No, that's not it. Thank you. Haa……."

Duan Diao cannot argue any further and backs down.

"Whoa! Master Cai! I passed! Over here!"

"Hey! You're hugging me secretly and don't let go! Master Cai, there's a girl there too?"

"Haha, congratulations. So Miss Jong passed too. It's truly fortunate that we're all entering together."

Duan Diaoya's feelings were further hurt by the sight of a young man flirting with two women.

\textit{I was already feeling sick from having to be polite to these horrible Zhongyuan guys, and then that guy called Azure Dragon already fell for it.}

\textit{If only I could just slaughter them all, leaving them speechless. I want to trample them all and throw them into the gutter.}

\textit{But! But more than that, the mission, the great cause of the doctrine, comes first… …}

Actually, it might be too much for Duan Diaoya, but he had the right to at least imagine wanting to do something like that. It's just merely a thought in his head anyway.

Duan Diao endure it and joins the team.

"Who passed?"

"I passed." "Me too." "Me, me! Master! I did it!"

The answer to that was three.

There were only three people accepter, three out of nine, including Duan Diaoya.

Furthermore-

"Hmm……"

Duan Diaoa groaned.

Why did these guys have to pass?

Two newbies. And why the half-assed one?

Ban Tong\footnote{半桶; lit. 'half bucket'} was clearly an alias.

This was a nickname with completely different meanings, usually giving the impression of a big eater who eats everything deliciously and heartily without being picky.

However, if you call it that with contempt, it means a carnivore that only eats food compared to its ability.

And Ban Tong belonged to the latter.

He was stupid, dull, and weak-willed. He was a man who was only used as a porter.

So, isn't it a half-baked, or in technical terms, 'eaten', half-baked …

Both rookies were new to this operation and can't even tell the difference between heaven and earth, and the only veteran was Ban Tong on a difficult infiltration mission?

Suddenly, Duan Diaoya's heart sank.

\textit{Did Wulin Alliance noticed something?}

\textit{How did we manage to pass only one porter and two newbies out of nine applicants?}

But Duan Diao soon shook his head.

Because it was a ridiculous idea.

\textit{If Wulin Alliance had known, they would have arrested and tortured us instead of allowing us enter the entrance exam.}

\textit{Didn't that bastard from Wulin Alliance just offer some pathetic consolation, as if he didn't even know my true identity?}

\textit{So, I was just unlucky.}

\textit{Or they just pick the ones that seem easy to deal with, oh, I see, those dark-hearted Zhongyuan guys were like that.}

Duan Diaoya sighed deeply.

The Heart Demon King was enraged by the disaster of Mahi, so it was impossible to retreat and say that the operation had failed.

So, somehow, they have to get it done.

Those above were coercive, and those below were incompetent.

It was the sorrow of a middle management.

Meanwhile, in another place.

"All three passed? That's great."

This plan to enroll Sado Geon-a in the Jeongmu Academy and plant a spy in the Jeongpa martial arts world had been in preparation since the Jeongpa martial arts competition last year.

Are you opening a school?

Then, of course, we have to plant a spy.

Actually, it's not that new.

Since both Sadoryeon and Wulin Alliance were desperate to plant spies in each other, it was also true that they both knew that there were several spies among their subordinates.

But this opportunity was different.

If you just perform well at Yizheng Martial Study Hall, you can join Wulin Alliance's combat unit, and if you can form a friendship with the precious young masters as advertised, what greater feat can there be?

But?

Then was there any reason to continue spying?

So, they were specially prepared people.

By special, I meant that he had not held on tightly by coercive means such as violence and threats, as the Apostles usually do, but had held on to his heart by bestowing grace.

The number of people gathered with such difficulty was three.

In fact, there were many who received such grace, but after being shaken and tested through many temptations, only these three remained loyal and did not betray until the end.

However, he only has loyalty and his martial arts skills were not particularly high.

Well, if he was someone who was good at martial arts, he would have made a name for himself and sold his face long ago, so it was inevitable that he would deceive the Wulin Alliance.

So I was worried about being eliminated, but what a surprise, all three of them passed.

So how can I not laugh?

The leader of the Apostolic Corps' combat unit, Osanmyeong, smiled happily.