\chapter{Journey to Kunlun (2)}

The mountain that stood between Xining and Qinghai Lake, east of Qinghai Lake, was Ilwol Mountain.

Long, long ago, when the Tibetan Empire was at the height of its power.

It was said that at that time, Princess Wencheng of the Tang Dynasty was sold to Tibet as tribute.

Meanwhile, Princess Munseong cherished and wore the precious mirror with the sun and moon engraved on it that she had inherited from her mother.

But, saddened by my situation of being sold to barbarians, I ended up destroying it on the way.

It was not known why the poor mirror was broken, but the legend goes that this mountain became known as Ilwolsan because the pieces of the mirror, the Ilwol Mirror, were scattered across it.

By the way, what about the life of Princess Munseong, who was sold to the land of Seojang while being dragged around like that and breaking all the coma?

From then on, they lived happily ever after.

The famous Potala Palace was built in Tibet to house Princess Wencheng.

Far from being treated coldly, he was treated with the utmost respect as a guest of honor.

Even my husband was so kind.

Originally, Tibet had a makeup practice of painting the face with red clay, but Princess Munseong hated it so much that she banned it by national law, completely eradicating the custom.

Anyway, this was the new home of the Kunlun sect, Mount Ilwol.

There were even attempts by Kunlun sect members to quietly change the name of the mountain where the Kunlun sect was located, saying that it was Kunlun Mountain itself.

Although it was an ancient name, it was inevitably given up because it was associated with the royal family.

Anyway, so Sun and Moon Mountain! Kunlun School!

The first of the famous SamQingmun Gates in Kunlun, TaiQingmun Gate, was crowded with visitors.

It was winter, and there was nothing to do, so Seonyeong was full of temples and mosques, so people who believed in orthodox Taoism flocked there.

Even though it was called a gateway, it was only a large door frame and there were no walls or doors attached.

Kunlun sect Taoists wearing Taoist hats and white robes with clouds engraved on them were standing with a dignified air, their eyes strained for no reason as they looked at the guests with serious expressions.

It's not strange or funny.

Well, it would be weird if you were laughing so hard.

As Qing approached, the eyes of the Kunlun Taoist priests, who had been wearing strict and serious expressions, widened.

The most beautiful woman in the world recognized by the people of Jiangnan, BingXuehwa, a nympho with an incomparable lewdness, and a man with his face hidden by a hat.

It would have been difficult to pass it normally, but fortunately, there was one person who recognized her.

"Aren't you Young Lady Heavenly Blossom Sword?"

"Oh. Have we met before?"

"Haha, no! I only saw you once during the martial arts competition, but I've never actually greeted you. I, the Kunlun disciple, greet the Elder."

Bungyeol takes the whip and gives a polite greeting.

"I am Ximen Qing, an outer disciple of the Divine Maiden Sect."

"I'm Xue Iri, the head of the North Sea Ice Palace Wulin Alliance Liaison Office."

"Peng Daesan of Peng Clan."

"Huh? Um? My name is Jian Buxi from Xuega Sanghoe."

It was greetings that followed the custom of the Orthodox Wulin, so there was no need for Jian Buxi to do the same, but since no one had explained it to her, she seemed to think she had to do it.

For reference, the reality of the North Sea Ice Palace Wulin Alliance Liaison Office was as follows.

No office, no operating budgets, no work, just one person. Also known as deskless in technical terms.

"I apologize for coming to Kunlun so suddenly. I had originally intended to stay in Xining and deliver a notice first, but I have some urgent matters to convey to Jangmun Jinin, so I had to head here first."

"If it's urgent news, then um. I see."

Boongyeol, seeing Qing's serious expression, nods his head seriously.

Of course, it was serious news, but that does not mean that Qing needs to act so sternly and seriously as if he was in danger.

But this was a matter of etiquette, and a stiff expression was a nonverbal expression that means bad news.

So, Bungyeol also guides the Qing party to climb Mt. Ilwol.

The second of the three gates, SangQingmun, was where the Kunlun school's Taoist temple begins, and the proper main gate of the school was SangQingmun.

First, he stops by the Kunlun Sect guesthouse and says that he will deliver a message to Jangmun Jinin if you wait a moment, and then leaves.

It was meant to give them time to unpack before meeting the elders. It also gave them time to get ready before meeting the elders.

After tying my hair back up and changing into the Divine Maiden Sect winter uniform, I was ready to pay my respects to Jangmunin.

Qing, who had finished preparing, was munching on the snacks that had been served in the guest room, and next to her, Jian Buxi was constantly putting snacks into her younger brother's mouth.

-No, who is this! Isn't it Jade Kirin!?

It was a loud, booming cry, but the voice was clean and not noisy, and the pronunciation was clear, making it a pleasant cry to hear.

"Brother Bengshi."

"Haha! What brings you here!? It must have been quite a journey to get to the border! Since you've never had a hand before, I'm truly delighted to see you!"

"You don't seem very happy."

Peng Daesan answers with a faint smile.

Then, Bengshi opens his eyes wide and then, "Haha!" he bursts into hearty laughter.

"This guy? When did he get so sly!? Wow, he's really improved. He's become more focused, so how wonderful to see! Yes, you're growing, too. I'm so proud of you, it's wonderful to see you…"

And then suddenly, another stream of tears flowed down my face.

Kunlunjae Ilgijae Dew Jade Sword Bengshi.

The man with the most tears in Zhongyuan.

It was said that it cries when it was happy, when it was sad with a very low threshold, and even when the food was delicious, so its nickname was Dew Jade Sword, the sword that sheds tears.

This was the very reason why people say that Peng Daesan doesn't look that happy. They joke that since he didn't shed a single tear when he saw him, he must be happy in words.

"Oh, you're not Miss Ximen!?"

"How are you, Young Expert Bengshi?"

Since Bengshi was not a name but a title or pseudonym, it was not called by abbreviation.

To begin with, the three major disciples of the Kunlun sect were all descendants of the Beng family, so calling him Young Expert Beng here had no discernible meaning.

"Master said he had a welcome guest and asked me to invite him to Jangmun Jinin! He was indeed very welcome!"

He looked really happy.

However, since we only met face to face and exchanged names at the Yongbong branch, I wonder why there was so much to be happy about.

Qing didn't know about it, but the Kunlun sect disciples were originally very affectionate and happy.

To begin with, Kunlun was located in a rural, remote, remote, and strange corner, so it was not easy to see the faces of acquaintances, so there was no choice.

"It's been a while since I've seen you, Young Lady Xue!"

Xue-i-ri nodded to him once.

Xue-i-ri only showed that she understood with a proud expression.

"Haha! You're still so reserved! But you've put on some weight, so it seems you're doing well!"

A furrow forms between Xue-i-ri's eyebrows at the abusive language that lacks any trace of delicacy.

It was the deepest value ever recorded in the history of Xue-i-ri observations.

"Young Lady Ximen. That flesh."

"Yeah. Unfortunately, that's true. Your cheeks have gotten a lot swollen lately."

Xue-i clenches her fist at that.

Xue-i-ri, who followed Qing, who was serious about eating, and her eating volume increased by leaps and bounds, so you could say it was her own fault.

"Oh, what beautiful lady is here!?"

"This is my Sworn Sister, Jian Buxi. Yi-mei, this is Taoist Bengshi."

After that, with the sound of the bell ringing loudly, waking up the silent winter passage, as the background music, I passed through OkQingmun, the last gate of SamQingmun, and headed up to the peak.

After passing the SamQing Palace, the main temple of the Kunlun sect, the residence of the Jangmunin appears behind it.

For some reason, old Taoist priests tend to end up with similar appearances.

Of course, the old Taoists may feel wronged.

Of course, just as monks go bald, Taoist priests also grow beards.

But you also need to grow your beard well.

Since you can't look like a bandit, you should only take good care of your chin and philtrum and trim off the messy part below your ears, and eventually you'll end up with a similar look to a Taoist beard.

If you put that on, it's only natural that you'll end up with similar faces anyway.

In that extension, the Kunlun School leader, Cheon Feizi, also looked like a Taoist priest who came straight out of a painting.

A nicely grown white beard.

And long, drooping white eyebrows.

What the heck? How do you grow eyebrows like that?

Qing has amazing eyebrows every time I see her.

I can't help but have a reasonable suspicion that perhaps learning Taoist martial arts might have the side effect of causing men's eyebrows to grow.

"Ximen Qing, an outer disciple of Divine Maiden Sect greet Tian Feiji Zhenren\footnote{眞人; a Taoist that had attained enlightenment}. How are you, Elder?"

"Oh, my dear. Our Youngest Sister is here. Is Senior still in good spirits? Last time I saw her, this junior seemed much older."

"Yes, she's very well. She's still flying on her sword and all."

"Hmm. I wish she'd be a little less springy. So, how's your training going these days? Have you achieved anything, even the smallest accomplishment?"

"Oh, that's…"

Qing hesitated for a moment, but then decided that it was right to tell Jang Moon Jin.

"I got into harmony last fall."

"Yes, yes. You've already broke through the wall, so there's no need to rush. You still have plenty of time left, Youngest Sister, so don't be discouraged, okay?"

It was just a common courtesy, a plain greeting, and a strange answer from a common person.

"Wait, you said you got into harmony?"

"Hehe. It's embarrassing, though."

"Unrestrained Realm!"

Tian Feizi shouted without any sense of propriety.

\textit{What do you mean, Unrestrained Realm?}

\textit{A child who was at her peak last year, now she's in harmony in just one year? Does that make sense?}

\textit{In the history of martial arts, this, no, can this be applied to the history of martial arts?}

\textit{Is this child joking with me?}

\textit{No, since she's the Senior Female Mad Dog's diciple, then that kind Cheon Hwa-geom wouldn't dare try to deceive an adult.}

\textit{No, does it make sense to reach Unrestrained Realm at twenty-one?}

It was the principle that we must look at the world broadly, observe all things, and, although we cannot precisely define and express the essence of a person, we must vaguely feel it in our hearts, organize the world into one, and establish ourselves.

However, Tian Feizi was also a Taoist priest who was in charge of the Gupa branch and the Kunlun branch.

The surprise was fleeting, and he quickly regained his composure…

He could't.

\textit{Even if I think about it again, it doesn't make sense.}

\textit{Only twenty-one.}

\textit{How can I skip my training and drink the alcohol I've been saving? Isn't this the time when I get really caught up in such foolish worries?}

\textit{They were just big kids in their twenties, they were adults in age but still have no sense of humor, and when they do cause accidents, they only cause big ones. Aren't they the troublemakers?}

\textit{It would be different if Heavenly Blossom Sword had reached her peak around the age of fifty.}

\textit{But the realm of ascension was to stand in a higher position and discover a future that was much more difficult than the present.}

\textit{In a year, in Unrestrained Realm? In a year? Twelve months, no, since it was autumn and a leap year, fourteen months? Fifteen months? Sixteen months?}

\textit{No, but does that make sense!}

"Elder?"

"Oh, right. Congratulations. This is truly a great fortune for the Orthodox Wulin. Well, congratulations. Our Yungest Sister is truly admirable…"

It was a bit of a daze for some reason.

Although they were of the same age only in terms of generation, she was still very polite and dignified, and her attitude towards adults was lovely, so he called her Youngest Sister out of affection.

Now, it has reached a level that was truly worthy of being in the same rank. But.

Then suddenly he started to worry.

\textit{Even if it's a great accomplishment, she's too young.}

\textit{If even I, who have cultivated myself, can suddenly feel jealous, how much more so must others feel?}

"Hmm, Hmm. Maybe I'm worrying too much, but you should be careful about letting the world know about it."

"Ah. Both Master and Alliance Leader also said so. But how could I dare hide it from Tian Feizi Zhenren?"

"Haha."

Tian Feizi looks at the youngest of the same generation, who was much younger than her, and has a pretty smile on her face.

\textit{Seriously, what kind of monster is she!}

\textit{This was why all the worldly fathers were anxious because they cannot have daughters. Perhaps we should actively look for girls when taking in Kunlun disciples!}

He was thinking this, unaware that he was already smiling warmly like her own grandfather.