\chapter{Journey to Kunlun (5)}

Then, a thought suddenly occurred to Qing.

What? Doesn't that make sense? Nyenyeong, that guy's talking like he can just take out a zombie or something?

"But if resurrection was so difficult, what exactly were jiangshi? Self-reliant jiangshi? There were jiangshi that can think for themselves and even have memories."

"A sage of the spirits? Oh. That's a very rare record, you know it well. You seem to have an interest in sorcery, too. were there any records left at the Divine Maiden Sect?"

"Do you know about Jaryeongjiangshi?"

"Yes. There were such monsters. But jiangshi were monsters, not humans. How can the two be compared? Is reviving a person completely the same as turning them into a monsters?"

"A monster? But from what I've heard, it has memories and can think for itself. So, isn't it the same person?"

"Humans and demons don't think the same way. There were immortals in the celestial realm who have ascended to heaven, but their thoughts differ from those of ordinary people. Just because immortals have earthly memories and can think for themselves, do they count as equals? Absolutely not."

"I don't know because I've never met a hermit. Oh, no? Have you met one?"

He spoke while recalling the annoying old man he had encountered during his tour of Qing's Jeolgeombyeok, who he didn't know was either the Great Emperor Mucheon, the Great Emperor Mucheon himself, or a remnant of his thoughts.

"Huh, huh, keuhh."

Danlun Zhenren kept making a sound that sounded like he was laughing.

But looking at his expression, it wasn't a mocking laugh, but rather a smile that brightened his normally blunt face.

"That was a funny joke. I'll have to remember that. Hehe, right. Hmm, Hmm. Big, phew."

It must have been quite fun.

I don't know what's so funny about it though.

"Then how about this? The soul of the body's owner has returned to the body, but it's already passed through the reincarnation gate and lost all memories. was that the same person or not?"

"Well, some people say things like, 'If you look at it, what's it like to have a past life?' was it possible to regain memories?"

"Absolutely impossible. Even for a sorcerer who has reached the semi-virtuous realm, this was true. I said nothing was impossible in sorcery, but I take it back. A soul that has passed through the gate of reincarnation can never regain its former memories. To put it bluntly, it's like melting down the metal of the soul, turning it into an iron ingot, and then creating a new weapon. The affairs of the underworld aren't that lax. How can one govern the affairs of the Three Thousand Worlds of Saba with such a mindset?"

The three thousand in the three thousand world does not refer to the number three thousand.

The thousand worlds were called the thousand worlds, and the small thousand worlds.

A thousand worlds, a thousand. Two thousand. A thousand worlds.

If you gather these two thousand and one thousand, it becomes the three thousand great thousand worlds. This was the Buddhist Saha called the three thousand great thousand worlds.

In other words, if you multiply one thousand by three, you get three thousand worlds, which means ten billion worlds.

So, in front of the law that governs the three thousand worlds, humans were nothing more than a speck of dust. No matter how strong the will of dust is, it cannot resist the law.

"But shouldn't you ask the weapon's owner about that? Even if others say it's not the same, if the owner says it's the same, then it's the same, right?"

"Hmm? Even if you melt down a weapon and create a new one, if the owner was the same, then it's still the same? Oh, well. That's, um. convincing. No, it's not. If you think about it, what was the law of Saba? It's all about the mind. What I see and think was the phenomenon. Ah, right, so that's what it is…"

For a moment, the focus of the single wheel suddenly goes blank.

Sitting cross-legged uncomfortably on a chair, with your hands clasped slightly in front of your lower abdomen, a moment of pure Taoist energy surges through you.

No, what was it? Realization here?

Why am I asking you this when you were the one who has attained enlightenment?

This old man, you've been thinking only of yourself lately?

How much time has passed like that?

When I opened my eyes, they were clearly different, and my eyes started to change into a subtle, similar shape.

A complete transformation!

I don't know why it was decided to unify with the small eye instead of the big one.

Well, that was because I was a simpleton who enjoyed the hobby of writing in a dark study on a cold day.

Because having smaller eyes was beneficial for eye health.

Other than that, it looked pretty boring.

For the martial artists from prestigious schools who have learned martial arts since childhood and whose bones and muscles were tuned for martial arts, even if they were said to have undergone a complete transformation, there was not a very strong reaction.

This was because the body was already optimized to a certain extent, so even if further optimization was achieved, there will not be a huge change.

Of course, if you have an accident or a defeat along the way and your bones were twisted, you will become extremely vulnerable as the chaos will start.

If the enemy looks like that, I learned from my master that I should kill him immediately without delay.

I wonder if about this much has passed.

Danlun Zhenren opened his eyes. No, did he open them?

The one eye that was thin and the other was less thin was unified towards the thinner side, so he was a single-eyed Zhenren with narrow, squinty eyes and a very suspicious appearance.

And then he looked at Qing and smiled with an unusually suspicious smile.

However, it was polite to bow and greet each other.

"thanks."

"Hey, was that something you should be thankful for? Congratulations on your enlightenment."

"I was just starting to feel my joints starting to ache. It's always better to delay a complete transformation, so I've truly struck it rich."

Of course, the body will optimize itself and regain some of its youthfulness, and the older you get, the more it will return.

Is that usually considered a benefit?

If you reach your peak at a young age, your body will not age easily and will be strong, so in the end, it was much better to achieve it as early as possible to delay aging and stay healthy.

"Huh. Now that I think about it, you weren't a sorcerer, were you? You trained in martial arts?"

"Hmm? Why would you learn such useless magic when you could have the precious martial arts of the mysterious Kunlun? It's just a pure hobby."

"Oh, useless."

"Magic was the act of twisting common sense into sophistry and manifesting it as a law. So, ultimately, it's just borrowing the power of others. Furthermore, great magic requires the alignment of heaven, earth, and human time to exert its power. Even if you achieve it, you'll be treated like a fake Taoist master. Why learn it? After all, I'm a disciple of Kunlun, so if I wanted, I could acquire the world's divine powers."

"Hmm. I can definitely see why you said the alcoholic beverage was practically non-existent."

"Hmm. Good. So, where were we going?"

"Huh? was that the end of the climax of your experience?"

"I never really had much interest in martial arts. I just learned that it would keep me healthy for a long time. When I was young, I was forced to train under pressure from my brothers, and now I just enjoy brewing medicine and organizing old books. So, what? So, ah, we were talking about zombies."

"It's a self-reliant spirit."

"The character '자자' in '자령' means 'self', and '령' means 'command'. It's not about following a master, but about thinking and making decisions on your own. It was created by a group of martial artists during the First Demonic War, but it wasn't very successful."

"why?"

"I already told you. The zombies were not human."

The Jinju Eonga magicians only wanted to revive their comrades who had memories from their past lives and fight together.

But the problem was that the Jaryeong Jiangshi did not think of their past selves as the same person.

Most of them left, saying, "What does human fighting have to do with me?"

If we exclude the few who participated just for fun and helped, it ended up being a heartbreaking experience for the bereaved families.

The saying that when you become a zombie, you become a different person, a completely different creature from your past self, refers to this result.

Suddenly, Yun Yuanying's unpleasant confidence came to mind.

Someday you will understand yourself.

If that means turning them into zombies and having zombie mindsets, then well, that makes sense.

In the end, it seems like Nyeonyeong was the one who was the zombie.

Is it certain based on the evidence?

But the countless swords of that strong force.

Is that the power a zombie can show? Can something like that be produced?

"So, what happens to the realm of the Jalyeong Gangsi? was it restricted by the realm of the previous life?"

"I've heard that there's a certain aspect to it, even in terms of skill. Of course, a master swordsman would be skilled with a sword. However, I've heard that the quality of a qigong was determined by the skill of the maker and the materials used."

"So, what if the best shamans combined their powers and crafted a shamanic spirit using the finest materials? Could they possibly create a shamanic spirit with life-or-death-level internal energy?"

"I don't know. The Jalyeong Gangsi was a vision of the Unga. And the Unga were from the same political party, so if they didn't provide information, what would they have stolen or robbed?"

Rather, since the song was a political party, the remaining records were just old records.

"But how could someone not have lost their minds? Knowing what kind of Strange Monk Jaryeong Jiangshi was, yet still giving that inhuman, outlandish being such a life-or-death threat, internal energy— Ah. Right. Those damned Jiangshi bastards, they were out of their minds! That's right!"

It was a single-minded Zhenren who suddenly sighed.

He was still a simple-minded person who only explained things after finding out on his own.

"That Yun Yuanying kid. He was a very kind child, well-versed in magic. Even back when he was a patrolman, he was a young magician I often visited in Kunlun to discuss with him. I still vividly remember that time. Then I heard that he destroyed his family and joined the Blood Cult. I thought he had crossed the line in his fascination with magic, but what if the destruction wasn't accomplished with the help of the Blood Cult? A mortal with life-or-death-level internal energy? were you certain? Did you see it for yourself?"

I don't know what Nyeonyeong was like in the past that everyone she met called her kind, pretty, and pathetic.

"Yes. He said so himself."

"Did you warn the Wulin Alliance?"

"I relayed it to the leader, but since he's young, he didn't seem to believe it."

"Well, if they thought that child was human, no one would believe it. Heh. There's probably no record of the Jaryeongjiangshi."

Even during this great war, the Wulin Alliance was located in Chang'an, not Kaifeng, and the library was burned down due to the invasion of the Demonic Cult.

It was said that the information comes from the oldest ancestor's diary among the Kunlun books.

It was something that Danlun Zhenren, who had a hobby of transcribing and binding books by year, naturally came to mind while transcribing.

"If there were any records of our ancestors remaining in other sects, they could serve as evidence. I must report this to Meng immediately. But, rushing won't make a difference, so I need to finish the story first."

"Huh."

It was the Danlun Zhenren who acted as if something was urgent, but then looked at Qing calmly again.

"To conclude, the difficulty of the knight's sacrifice, the blood poison you speak of, was precisely this. Even though the knight may be a Strange Monk of the opposite world, he was still human."

Still, he was human.

Somehow, my heart feels hazy, that kind of feeling.

"There's only one record of the sacrifice being successful, and even that's by Dongbangsak, so it's not entirely credible. Therefore, such a Strange Monk likely doesn't exist."

Dongfang Shuo was an immortal in the folklore of Zhongyuan. According to Taoist legend, he was a Strange Monk who stole and ate all of the peaches of the Heavenly Way from the Queen Mother of the West and gained a lifespan of three thousand years, or one hundred and eighty thousand years.

Of course, since I had never heard of a story about the resurrection of the dead, this was precisely what was said, saying that it was not credible.

"Does this answer your question?"

"Yes, that's enough."

"Well then, that's fine. Hmm. I guess the binding was a bit messy for the time being. Still, it's not a bad thing since I've got a young magician friend again."

What? Since when have I been your sorcery buddy?

By any chance, was there really no one to talk to about magic?

That was the time.

As if waiting, a noise came from outside, calling out to Qing.

- Miss Ximen!? Did you hear the answer you wanted!? All the people who will accompany you to the Jeolgeombyeok have been chosen! If Miss Ximen comes, we can depart!

It was a call from the Bengshi who said he would leave only if you came.