\chapter{Journey to Kunlun (1)}

As soon as he returned to the mountain, Amukhaprap spoke to his companions.

"This duty to warn of danger was extremely important. It also requires the sincerity to minimize even a small part of your great self. You Zhongyuan bastards were inherently lazy, as I know very well. But please, this time, be a little more diligent, you who were born as cows."

And then, wouldn't you rather walk out of the mountain with your happy puppy?

At first, the group just kept talking nonsense and thought they were going to see Sophie or something.

It's been a while and it hasn't come yet. What was it? was it something big?

"But, Iri, didn't you say it wasn't tasty?"

"As I was eating, yes."

"Just boil anything and it'll be delicious."

"sure."

What, isn't Gunyeong's vocabulary gradually becoming richer? But yes, the emotion contained in those three letters, that sense of satisfaction.

That's not a compliment, Gunyeong…

And only after a long time, after Xue-i-ri had emptied about five bowls of Truth's Soup, slurp slurp.

I realized that Amukhaprap's words, "Hurry up, you lazy bastards," were the monk's own way of saying goodbye.

No, you're saying it's going to end like this?

No matter how urgent it is, in the middle of the night?

Anyway, one thing that drives me crazy was my ability to act.

Come to think of it, didn't I just rush out at the perfect time to go hunt down the bandits, and then rush off without even knowing anything about the enemy?

Tsk tsk. You have great action skills, but if you don't think, your body will inevitably suffer.

There were people who foolishly jump into anything without any prior knowledge, thinking that they will somehow be able to do it.

If someone had heard Qing's true feelings, they would have wondered, "What the heck, was this self-criticism? Why would someone I know do that?"

Unfortunately, no one in the group had the ability to read minds.

So the Qing party also cleared the battlefield.

(Meaning that he searched for wild vegetables.)

They said that all the people they captured were taken away by the lamas, but all they got out was money that they had each hidden away.

However, Xue-i-ri was the only beggar among the group.

Even Jian Buxi has a stake in the company, and although Qing doesn't know it, she was a precious person who was the great guardian of the new religion and the sister of Cheonma Jonhou.

I did find some snacks that I had hidden away to eat alone, but they were too disgusting to touch, so I ate them all and put them away.

At least it wasn't a waste of time.

"Hmm. Let's go now."

It was a shame that not a single kidnapping victim was rescued, but isn't this the way things were supposed to happen in Wulin?

First, gather all the ingredients from the pantry and pack them away, and make sure to thoroughly extinguish the campfire you lit to prevent it from starting a fire.

And then the Qing party leaves the bandit camp without any hesitation.

However, not everyone was foolish.

"Uh, us?"

"Please take us too!"

A bunch of those left behind.

There were some who have all four limbs attached.

However, the way Qing deals with evildoers was by first cutting off their limbs and throwing them away.

Tying it up requires rope and there were concerns about it possibly coming loose, but how simple and effective was it to just kick it with your foot and break it apart?

The night in Seonyeong was still deep, and the winter nights only become harsher until dawn comes.

Leaving behind such a heartfelt farewell.

Who would steal like that? Who threatened to steal with a knife?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Do you know that comfort of returning home on a cold night after a rewarding day's work?

Please take care of the bath water and make the face of the idle person brighten up.

After a good night's sleep, I wake up slowly, grab some breakfast that I haven't had in the central region yet, and then set off.

Henan County was an administrative district located in the southeast of Qinghai Province, covering approximately one-third of the entire Qinghai Province.

The north of the wide area was high and the south was low.

But the north was warm and the south was cold.

Normally, it would seem natural that higher elevations should be colder.

The lower part was a rugged mountainous area with jagged ridges and sparkling snow all year round, and the northern part of Henan was surrounded by a vast plain that stretched out across the Qinghai Plateau.

That means it's easy to move around.

Of course, even though it was a plain, it was quite bumpy and has many steep hills with round curves, but there was a road for horse-drawn carriages to travel on.

Thinking back on the entire hike up from Sacheon, it was just a comfortable road, no different from a flat road.

The group was running lightly, but their speed was by no means light.

Well, the level of the group was almost on par with that of a large sect in a medium-sized city.

Of course, Xue-i-ri was breathing a little heavily and was also sweating profusely.

After the sun sets, we enter a small town called Taekgo.

The next day, we went north and reached a tent village of the Jang tribe called Maeksu.

"We have an honored guest, but the granary was a bit tight until winter, so, um. I'm sorry. I feel embarrassed for stopping by."

Grandfather Jangjok expresses his regret, saying that it was difficult to continuously greet him in his fluent Zhongyuan language.

Hospitality was an apology for not being able to welcome you with a small village feast like the Jang tribe of Sacheon.

The Qing, who was weak to kindness, threw a feast by releasing the food they had brought from the bandit camp.

Departing early in the morning, leaving behind the enthusiastic farewells of men, women, and children from all over the village.

From here, we leave Henan County and enter Hwangnam County, and enter the small (large in Qinghai) city of Hwangnam, where the county seat was located.

Passing through Cheomchal and Bongganggu, a small village belonging to Hwangnamhyeon, to Pyeongan in Seonyeonghyeon, and Seonyeong!

Seonyeong was the capital of Qinghai Province and the only large city of a scale comparable to that of Zhongyuan.

First of all, the colors of the buildings were different. The walls were painted white, and the Buddhist temples in Jangjok were gilded with glitter.

And also, oh, what?

Why was there a building like this in Zhongyuan?

Qing exclaims in admiration as he looks at the temple with its round roof.

I'm really curious how this was built.

Rather than being a carpenter, he was a sincere Qing.

A unique feature of Xining was the presence of Hui people, a population not found in the southern part of Qinghai Province.

The Hui people were descendants of Westerners who believe in Islam, a religion of the Western Regions. In the Qing Dynasty's homeland terms, they were called Moslem.

However, the Hui people of Qinghai have been mixed with the Chinese people for a long time, so their appearance was exactly like that of Zhongyuan people.

The clothing was also of Zhongyuan style, with the men wearing a double-breasted hat, that is, a Muslim-style hat, and the women wearing a wide hat that looks like it was made of knitted fabric, while their faces were tightly wrapped in cloth, barely revealing their eyes.

It's a proper metropolis where you can enjoy all kinds of luxuries with money, and there's an exotic landscape that doesn't feel like Zhongyuan at all, and there's so much to see, so I'd like to get a room and spend a few days leisurely wandering around.

Because I don't have that kind of time.

"Hmm. Let's first check out Qinghai Lake, then climb up to Kunlun. I heard it's that vast."

"Are you suggesting we go to Qinghai Lake now?"

"Huh? Then you're not going?"

"Ah. Right. Xining is famous for Qinghai Lake, so I guess you thought it is nearby."

"Why? Usually, when there's a large lake like that, doesn't a large city grow next to it? What's wrong with it? How far away?"

Peng Daesan pointed his finger above her.

Although it was exotic, it was a large city, so the buildings were three, four, or five stories high.

\textit{Come to think of it, how did you manage to build four or five floors?}

\textit{What the heck? If you just bake bricks and stack them, it'll just collapse. Is there some secret?}

Qing had excellent qualities that would have made her a great civil engineer of the century if she had been a carpenter instead of a martial artist.

\textit{In fact, it was true that you can see as much as you know, so thanks to that, I was able to enjoy traveling alone twice as much.}

Not knowing that Qing was thinking of something else, Paengdaesan spoke with a mischievous smile.

"Qinghai Lake is up there."

"Huh? Where, oing?"

Only then did the focus of the scene shift from the towering buildings to the majestic mountain range in the background.

Even at a glance, you could tell that it was not an ordinary mountain, as it was covered in snow all year round and in the distance.

\textit{Are you saying I have to go over there?}

It was when Qing looked at him with a bitter expression.

"Customer? That's Mt. Gyerim. To get to Qinghai Lake, you have to cross the Bukhaeryeong Ridge."

The owner of a nearby stall corrects the angle of Peng Daesan's finger, which extends too far north.

Although it was high, the mountain was significantly lower than before.

Qing exhaled in relief, then looked at Pangdae Mountain with narrowed eyes.

"What's that, San? That's not the mountain\footnote{A pun. 'San' means 'mountain' }? Were you impressed by the fish cake? Maybe it's not this mountain?"

"Ahem."

"What? Was this your first time here? You seem so familiar with it, I thought you'd been here before."

It was Peng Dae-san who guided us to the Xining Jeilgaekjan Qinghai-ru (a name that was somehow very familiar and hazy to Qing), and it was also Peng Dae-san who explained about the temples and the Hui people, who were just different people from Zhongyuan who believed in different gods.

I thought you talked because you knew something.

"I just picked it up."

"Yeah, yeah. You studied hard because you want to be useful, right? Hey, there's no need to be embarrassed."

Qing pokes Paengdaesan's side.

"Isn't that something to be thankful for? Having a friend like this makes traveling so much easier. I mean, I also might be wrong once in a while. Why worry about it?"

"Studying? I just picked it up on the way. Why would I bother?"

But he turns his head towards the direction of the room and says this with his ears reddened.

That guy keeps coming and going.

Why was it that no matter where he goes, snacks were always running out, and travel information keeps pouring in unintentionally?

No, come to think of it, that's what San were like.

That's because your face was covered right now.

Why. A living legend, even in Luoyang, the floor was beautifully and colorfully embroidered with perfectly intact handkerchiefs.

Isn't that the jade giraffe that made Songok surprised, Ban-an shocked, Wi-gae kneel, and King Nanling throw away his mask?

For reference, Songok, Banan, Wigae, and Nanling Wang were the four most handsome men in the history of Zhongyuan, known as the Four Great Handsome Men.

However, according to the current Jungwon people's assessment, the Four Great Handsome Men were a thing of the past, and now we live in the era of the most handsome man of all time, Pang Dae-san.

So, isn't it natural that all kinds of snacks would be laid out like a flower path just by walking with your face exposed?

Why, those bastard followers-

"You have a really pouty expression on your face?"

"Huh? What? What is my expression?"

"You made that expression as if you ordered all the dishes, only five were brought to the table. No, I would even say normally five was all dishes."

"No, who would order five dishes just for the taste? Just one bite and they'll all disappear."

At that, Peng Daesan laughed.

However, it was Pengdaesan who even had a cool, low-pitched laugh.

"Do you usually taste something like that?"

"Well, that's because you're hungry. When you're hungry, anything tastes good. No, not just anything tastes good, but food. When you're hungry, anything tastes good. So, to truly savor something, you have to be moderately full and satisfied before you can objectively judge whether it's delicious or not."

"Hmm?"

"Besides, there's an order to how you eat food, so if you eat something oily or salty and then something bland, it'll taste bland and disappointing."

"What is the taste of regret?"

"So you're saying that if you don't eat it all, you won't be able to taste it?"

It was a complete lie, but on the other hand, it was strangely persuasive.

Peng Daesan got lost in thought, wondering why it seemed so plausible, and whether the act of tasting it was really like that.

anyway.

It was said that Qinghai Lake can be seen if you climb 200 li to the west and 650 zhang upwards.

It was an accurate tip from a local, a street vendor selling colored thread craft ornaments.

Qing frowns her clean forehead with effort.

\textit{No, why is the lake on top of the mountain?}

\textit{It's so damn far and high.}

\textit{No, the Kunlun sect is like that too. They settled down in places like this.}

If the Kunlun sect hears this, it will be very unfair.

It's like this since I moved.

Kunlun Mountain, more precisely called the Kunlun Mountains, was a mountain mass roughly the size of the entire Hubei Province.

Because among them, it was in a remote mountainous area where there were only mountains, mountains, mountains, and mountains.

Besides, it's not in Zhongyuan, it's in the Western Plains.

Because of this, Kunlun was often teased about being included in the Western martial arts world.

So, I think we've gotten incredibly close to this point.