\chapter{Journey to Kunlun (6)}

Based on the experience of the last cliff tour, everyone tried to bring as many people as possible.

If you say that it was the deep understanding of the Great Emperor Mucheon, it was a treasure whose value cannot be measured.

Experts and those who were stuck in a wall came out in droves, trying to get even a single piece of that truck.

But why was there not much people in the Kunlun sect?

Even if we tried, there were only nine people, and even the Qing party did not participate because it was a sect event, so there were only nine people.

They say the space was narrow, but how narrow was it?

Did that Great Emperor Mucheon get stuck in a crevice in a rock and swing his sword?

I can't even imagine, and I don't think that grandfather would have the personality to do that.

If you were swinging a sword in a place like this, you could have just collapsed the cliff, but you wouldn't have struggled in a narrow place.

"Ah. That's right. The single-minded Jinin attained enlightenment. It seems he began to reflect on himself while explaining it to me."

"Yeah, yeah. That's great. That's the second thing. Let's go. It's already a place where the sun doesn't shine, so if it gets any darker, it'll be completely dark."

He was a single-minded person who had become like that.

But everyone really doesn't seem to care.

As Qing was making a face like, 'Is this right? were you being bullied or something? Why were you stuck in a place where there's no one?', the representative of the three major disciples (selected without a vote) Bungsa-in gave an explanation.

"Well, the true master Danryun originally had no interest in learning, and now that he has surpassed the age of a thousand, it wouldn't be surprising if he were to reach the pinnacle at any moment. Everyone was assuming he would reach it by the end of the day."

It comes from the saying of Confucius, "When a man turns fifty, he realizes the meaning of life given by heaven."

This was derived from the saying of Confucius, "When a man was seventy years old, he can live however he wants without breaking the law, because he was that wise."

Hmm. Danryun Jindo was quite old.

I guess no one really had any expectations.

But somehow, the group started heading towards a secluded place and entered a narrow valley path that was only wide enough for one person to pass through.

It was a narrow valley that would require someone of Zhuge's size to hunch their shoulders.

Then at the end there was a small open space.

It was a small basin shaped like an upside-down cone between cliffs.

As it goes up, it gets wider, as if there was a hole in the sky.

I understood what Cheonbija meant when he said that the further the sky darkens, the darker it gets.

It's already dark because the shadows have fallen.

If the people who had gathered around him were not Taoists from Kunlun, it would have been a place where they could have punished him by asking what he was doing by bringing him to such a dark and gloomy place.

Qing looks around.

However, it was just a peculiarly shaped terrain, and there was nothing that looks like a sword mark.

"Is this the cliff? No matter how much I look, I can't see any sword marks."

"Really? were you blind? If you can't see with your own eyes, why were you wearing it? Did you wear it as an ornament to keep your blind fetus from being born?"

It's a sudden, harsh sound.

"Huh."

"Look at this. Again and again. If you saw an adult, you wouldn't immediately hit their head hard and shout a greeting. What the heck? Oh my, the future of Wulin was dark, dark. This bizarre Daemajin was going around claiming to be a female knight of the Jeongpa faction. What the hell was going on in Wulin these days?"

This series of brilliant (must be pronounced quickly) criticisms.

Come to think of it, this old man was like this last time too.

It had already been a year, so I had forgotten about it, but it was the thick, sweary rant of my grandfather that was piercing into my ear.

Qing tilts her head to the sound of the voice.

Oh, oh, oh, oh, up there, a pair of shoes floating in the air.

He was the grandfather of the Great Emperor Mucheon, or the Great Emperor Mucheon.

"No, don't be so hemp-y. And now I've taken a picture of Hwagyeong too, right? Goodbye hemp-y for good."

"Huh. If you're in the devil's mouth, you're a demon, and if you're in the fire realm, you're a Taoist? If a woman who kills people and laughs happily isn't a demon, then what the heck? Okay, let's hear it out."

"What?"

"What's going on in Wulin these days that they don't call a murderer like you a Daeman? Back in my day, even the slightest bit of cruelty was met with a lot of fuss about being a sorcerer or a demon."

"Ma'am, just do your work. Just a little."

Qing looks around.

What the heck, it got really bright?

In the past, the world was a gray world, made up of black and white shades, but now it was a landscape filled with vivid colors.

"Well, since you're in the Hwagyeong, you can see more. Oh, what a shame. If you were in the Myeongma, I could've just killed you with a single stroke."

"Are you sure this was really my imagination? I heard you became a god. Aren't you just coming down now to pretend to be a god?"

Didn't you hear this during the counseling session for the MuQingdaeje held in Jongnam a while ago (which included swearing)?

The mind reacted to the swordsmanship engraved in the sword marks, and the image of the Great Emperor Mucheon that Qing had always drawn was created on its own.

But, I don't think that's the case.

I'm sure you made a few slips of the tongue last time, too?

"That vicious woman was so suspicious."

"No. That doesn't make sense. What I saw in Jongnam was the Seventh Stage, so how did it connect? What? Was Kunlun the Nineth Stage?"

"How could that be? Those guys who can't even stand properly, what kind of idiots were they? Actually, I was thinking about just leaving them, but wouldn't it be pitiful to leave them behind when you're giving them each a gift?"

"Huh."

"But how long were you going to stay stuck underground? were you even practicing the Tontu method? Well, I'm glad that you, who saw this great senior, couldn't dare stand at the same height and ended up stuck underground."

"Huh? Ugh!"

Suddenly, my vision darkens and a powerful pressure weighs down my entire body!

Save the Heavenly Blossom Sword! This old man was definitely going to catch me! Somehow, I recognized him when he was ticking away!

Somehow, a vulgar laughter rings in my ears.

And after a while.

The earth in front of Mucheon Daeje shakes.

And then, with a bang, the dirt and gravel flew up high, and Qing's upper body, panting heavily, rose up.

"No, what was it? were you filling up the land now?"

"Okay. Sit down."

As he did last time, Qing slams his huge butt down onto the ground with a thud.

As the Great Emperor Mucheon beckoned, a huge sword flew in and swung around.

The Great Emperor Mucheon sits on it, crossing his left leg over his right thigh and sitting crookedly.

"Still, was it a bit softer than last time?"

"I told you it was your own doing. Back then, you were so desperate to be cursed, but now it seems you're not so desperate."

"Hmm. It's gotten a lot better."

"If Hwagyeong's martial artists forces were still acting like that, we're in big trouble. Isn't killing people less fun now?"

"No? It's still thrilling. It's always the best."

"You're talking so rudely, even though you have a pierced mouth."

"You said it was my heart anyway? Even if I lie, this bitch will just start swearing at me and swearing at me, saying I'm lying now, right?"

You have the talent to read people's minds.

"Huh? You're going to eat me like a friend just because you're a little used to it?"

"Oh. Now that we're on the subject, do you want to be friends?"

"Okay. What comes to mind when you think of Kunlun?"

He was a muQing or mucheon daeje who would immediately change the subject if he heard anything even slightly unfavorable or unpleasant.

"I didn't ask. I know you're stupid anyway, so there's no need to bother with your brain. Isn't that the Unryongdaepalsik?"

"Well, it's purple."

"Huh. What about purple? If the person using it was purple, even if they wield a third-rate martial art, it's a world-class martial art. If you teach a village idiot a new art, will he suddenly become a peerless warrior? Well, if you just keep hitting him, he'll probably be able to take down Hwagyeong somehow."

"Huh? I just hit you-"

"Excluding Unryongdaepalsik, Yongbongdaegusik, Yonghyeongboe, TaeQingmusanggeom, TaeQingganggi, and Chumyeongdo, Jonghakgeumjongsu, Unhakjang, Nakankwon, Unryongjo, Yongmuseonhoegak, and these guys were some fucking sect that uses hooks. It's a hook-throwing martial art called Galmigu. Now that I've said it, even you, the stupid bastard, understand what the problem is, right?"

"Miss, just say what you want to say. As for my answer, I have no idea."

"Are you not even going to think about it anymore? What on earth were you going to do with this?"

The Great Emperor Mucheon presses the air with his index finger.

Then, in response, Qing's head also tilted back.

"No, isn't that a Gyeonwolmangji? You said this isn't a traditional Korean herb. When you carved the knife marks here, it wasn't even made yet. was it right for Grandfather to use it now?"

"You don't even bother to think about the problem I gave you to solve. You're completely focused on whether I'm real or not. Why should I explain it to you in a plausible way? Since I emerged from your imagination, was it strange that the owner of the Gyeonwolwangji, which you already know, was using it?"

"It's really incredibly suspicious."

"Did you think I just randomly decided the order of the first steps? I'd already completed the first step and been back, so I already knew everything when I carved it on my wall."

"If it's too logical, it's actually strange."

"Think about it a little. Do you really want to look so embarrassed and lost in front of your juniors? You've already practiced thousands of times and etched your best form."

Suddenly, the image of Emperor Mu-Qing swinging his sword, adjusting the angle of his body alone to look cool in front of his juniors, flashed through my mind.

"Oh, a little. The part that used to be cool was starting to feel strange. I'm slowly losing respect for it."

"That's it. Those Kunlun sect guys only think about flying around on empty days. Well, I understand, since their original neighborhood was so dangerous that they couldn't walk around. So just look at the martial arts names. You know names were important, right?"

"If you look at it that way, martial arts were also sorcery?"

"Yes. So, dragons, phoenixes, cranes, clouds, and even the clear blue sky. Climbing up and down the rugged slopes of Kunlun Mountain, how much must you have yearned to fly?"

"Hehe. I've never been to Kunlun Mountain. Actually, I tend to look down on mountains."

"Have you been to Mount Huashan? Compared to Mount Kunlun, Mount Huashan was just a flat hill, a hill."

"ah."

I completely understood it in one go.

That volcano was a flat hill.

What kind of lives did the Kunlun sect masters lead before moving?

"Well, it's a real struggle. Why go to such a remote, rural area? No, the countryside was where people live. Why would you go to such a remote place? You went into such a rough place on your own, just looking up at the sky, wishing you could fly, thinking only of your own comfort. Pathetic bastards."

"Don't the Jongnam faction members also look only at the sky? Of course, they look at the night sky, or more precisely, the stars."

"It's different with Jongnam. The Jongnam faction only looked up at the sky after I'd firmly planted my feet on the ground. They didn't flit around aimlessly, looking at the sky like the Kunlun faction, who didn't even know how to stand properly. Like you, you bastard."

"No, why were you suddenly swearing at me again here?"

"Huh. I thought he must be a bit of a jerk since he just moved in, but when I asked him, he just kept making excuses."

Kunlun Mountain was just a remote area where no one lives.

Rather, the Demonic Cult of Cheonsan can see the Silk Road from the Western Regions to the north and Zhongyuan to the south.

So, the biggest problem that the Kunlun sect faced was recruiting disciples.

Martial arts were better learned at a young age, but to take on even one disciple, you have to walk four thousand li to Zhongyuan.

Going to pick up a disciple was picking up again, and when will you come back!?

He went alone, and came back with a young disciple who had just started martial arts by his side.

Qing nods after hearing the explanation.

"Then it might be worth moving."

"Who said we moved? She was hunched over like a bitch and made excuses like, 'No, we really had no choice.'"

"sure?"

"If you've moved, you should be able to confidently say, 'That's why we moved. Why were you dissatisfied?' Why can't you be upright?"

And then, Emperor Mucheon snorted and looked down at Qing with a pitiful look on his face.

So, Qing feels very wronged.

Why were you talking about the Kunlun School and scolding me like that?