\chapter{Journey to Kunlun (3)}

Unfortunately, it wasn't just a time to enjoy a cup of tea and look at my beautiful granddaughter (the youngest of my sisters).

"Actually, I have something urgent to tell you, Sect Leader. On my way here, I heard that there's a gang of bandits on the rise near Henan."

"Oh, tsk tsk. What kind of bandit in the world would dare to commit a crime in front of the Alliance headquarter and the Shaolin Temple? Is there a trend these days in Zhongyuan to attempt suicide like that?"

"Ah. Not that Henan Province, but Henan County, which was all the way south from here."

"Oh, silly me. That Henan, that rural Henan."

It seems they call that place rural Henan.

Since it wasn't exactly wrong, Qing quickly agreed.

"Huh? No, you mean you came up the Sichuan Trail in this cold weather? Hmm, it's good to be young."

"I stopped by Sichuan to drop off Lan-Ah and pick up some poison. Um. No, that's not it. It's something more serious."

"I see."

Tian Feizi, who had been smiling bashfully, finally straightened his expression to look serious.

She told the story she experienced and heard in Henan County.

There were some suspicious bandits in Henan.

But as it turned out, they were actually the monks of Xizang and the monks of Nanning who had come to make money.

And even the attempted invasion of the Xizang Wulin stopped by the Strange Monk who came to subdue them together through interrogation.

"What? Something like that, um, then, what should I do? Ugh, what should I do about this?"

The Count was greatly embarrassed.

That was understandable, as the Kunlun sect has never experienced an external invasion since its establishment.

Before moving, the Kunlun sect was located in the Kunlun Mountains.

What kind of land was the Kunlun Mountains?

It was a remote area that belongs to the Xizang land, but even the Xizang people do not set foot in it!

A countryside that even country bumpkins don't go near!

Even in the outskirts, it was a outskirt that was treated as a outskirt!

To begin with, it was only three thousand li in a straight line from Cheonsan to Kunlun Mountain.

It was the shortest distance of three thousand li, having to cross the desert and the Kunlun Mountains, which were 1,500 zhang high.

If you go two thousand li, you have to go back and forth between the two largest cities in Qing's hometown by national road, and then go again to get exactly three thousand li.

So, Kunlun Mountain was a land that was not even needed by the devil and was not visited.

Even while the Demonic Cult was attacking four times, he jokingly said that the chaos of the Great Battle of Jeongma was over while he was on his way to support them.

From Kunlun to Xining, where I have now moved, the distance was 3,600 li, and from there to Zhongyuan, it was another year.

Even the Taoist priests couldn't live here. It was simply not a place for humans to live. It was an unprecedented event in the history of martial arts where a sect abandoned its own headquarters and moved.

The reason why he was the only one was because there was a force that moved before him.

The reason why Nokrimchae, who abandoned Nokrim Mountain and moved to Cheonjasan Mountain, broke the first one.

Of course, the reason was the opposite, because if they continued to settle down on the Lulin Mountains that spanned Henan and Hebei provinces, they would be crushed to death by the Wulin Alliance below and the Imperial Palace above.

Well, in conclusion, it was a failure again.

They were not particularly new, as they were the ones who constantly repeat the cycle of destruction and rebirth.

"These Xizangs, these Xizangs were coming to attack? Call your disciples immediately, but if they attack while you're on your way to summon them. First, let's inform the Alliance and ask for help. Heh, I don't know if we'll be able to get there in time. The road to Sichuann was blocked. Should we send someone to the nearby Kongtong for now?"

"Jang Moon-jin, calm down. It's not like the Xizang Wulin was going to attack right away. And Yumo-, I mean, the Strange Monk  said he'd do his best to stop them."

"Ahem."

It's Tian Feizi who suddenly came to his senses.

He coughs loudly in embarrassment and pretends to clear his throat.

"I've made a fool of myself. I was so shocked by the shocking news that I couldn't help but panic. Haha, what a fool! This was how my fifty years of training were wasted."

"No. You might be confused. Isn't it even more strange that someone responsible for all members of the sect would be so detached and calm in the face of danger? Even if just one disciple were injured, it would be painful."

"Hmm. I'm so grateful that you said that, Youngest Sister. Thank you…"

How on earth can you speak so beautifully?

If it were the Senior, she would have thrown a punch first and then cursed at Jang Moon, saying, "How can we take care of the others if he keeps acting like this?" and then thrown another punch.

A disciple who was truly more than enough for his senior. Truly, even His Majesty SamQing was too much. How can he bring such great fortune under his senior? I can't help but feel regret and resentment.

"Yes, I guess I'll have to take care of what I can first. I'll have to reorganize the main headquarters' formation, repair and raise the walls, and prepare a defensive plan."

"Oh, by any chance, would you like to report this to the authorities…"

Then Tian Feizi smiles sadly.

"I know. Aren't we Taoists who pray for the peace of all peoples of the world every day and perform rituals? If we were to pass on this cruel karma to the innocent just because we don't want to see our bloodshed, we wouldn't even be worthy of being Taoists."

It wasn't a smile, it was a sad smile.

It was said that a thorn in one's finger was more painful than someone else's slander, so the person who said that would not be at ease.

"Perhaps our settlement on Mount Ilwol was all arranged by the Primordial Heavenly Being. Haven't we settled in a truly exquisite location?"

There were two ways to get from Qinghai to Jungwon.

However, the southern Sichuan-Hanjung mountainous region was famous for being an impregnable and rugged terrain, and the northern part of the fork in the road ends up being a public mountain.

If you go down like that, it's Sacheon.

Isn't this a terrifying land where three great sects, the Amipa, Qingseongpa, Sacheondangmun, and Jeongpa, were located?

The only intact passage was the gently rolling hills east of Seonyeong.

However, it was Ilwolsan Mountain located west of Seonyeong.

If we leave it alone, we will have enemies in the rear, and if we touch it, the headquarters of the old sect was itself a natural fortress.

If I don't take care of my expression, it's really obvious what's on my mind.

Tian Feizi chuckled as she looked at Qing's expression.

"Come to think of it, there's no need to worry too much. Even our seniors from the previous generation are still quite well-off. If there's an invasion from the Saiwai Wulin\footnote{塞外武林; 'Beyond the Great Wall' Wulin}, there's no reason for them to remain in hiding."

The masters of the current Wulin were, in terms of Qing's homeland, like nuclear weapons.

If those masters directly takes action, another master of the same level would inevitably appear on the opposing side as well.

Those masters were known as the Ten Masters of Wulin, with a ratio of six to three. The Orthodox was six and the Unorthodox was three.

Of course, the general consensus was that there were bound to be more people who were hiding their true nature.

Even in the case of Talmyeongdo, he pretended to be a Transcendent Realm the whole time, but wasn't he caught by chance?

The argument escalated into a fight between people, and the master of Unrestrained Realm was cut down with a single blow, and his true nature was revealed.

But what if Xizang's Wulin invades?

The current Profound Realm masters didn't need to worry about anyone else's opinion, and as a master had his own responsibility, so there wasn't a single person in Tian Feizi's opinion who would ignore Kunlun when it was in danger.

Thinking this far, Tian Feizi felt a little more at ease.

\textit{Hmm. I think we shouldn't invite Senior Female Mad Dog.}

\textit{No, no.}

\textit{Even the Xizangs need to taste the bite of a mad dog.}

In fact, if we're going to judge women by their treatment, isn't there no place better than Zhongyuan?

Those barbarians don't even treat women like people, so if you insist on being cruel, you should just go ahead and kill those barbarian bastards.

Surprisingly, Tian Feizi's thoughts were correct.

In this era, no country exists that respects women as much as Zhongyuan. (Tribes may exist, though.)

Of course, being better than others doesn't mean it's okay.

"Is that why you came running so quickly? I'm truly grateful for your kind words. If so, send a message to the Wulin Alliance on your way back—"

Then, Tian Feizi waves her hand.

"No, no. Since you're already here, you should take the time to relax, take in the sights of Qinghai Lake, and enjoy its unique scenery. Why would you want to just go back after coming all this way? I was so impatient I almost made a mistake."

"If you're preparing for defense, you'll need a few extra hands. If there's anything we can do to help, we should."

"Your words are truly appreciated. But Kunlun's disciples were said to be the most talented martial artists in the world. So, don't worry about it and just have fun, huh?"

Tian Feizi was about to let her go and play with a happy smile, but then, huh?

"No. If you met the bandits in Henan and learned that they were on their way to Kunlun, then wasn't Kunlun your destination from the start? So, what brought you to this remote area? If it's a request from our Youngest Sister, no matter how difficult, how could I refuse it? Tell me frankly."

"Ah. Yes! I was going to ask about sorcery, but do you happen to know about the Dead Blood constution?"

"Oh, wow. When it comes to sorcery, the Eight Immortal Palace of Kunlun is truly the best in the world. Of course, those of us who were not educated know very little, but go ask the Taoists of the Yeondan. They're so impatient that if you ask them, they'll be so welcoming that you'll regret asking them, and they'll keep you entertained and explaining things to you."

"Hehe, thank you. Oh, and also, I would like to ask to see the Absolute Swords Cliff of the Great Emperor Mucheon. Could you possibly allow me to do so?"

"Ah! Right! I completely forgot about that! I thought if Youngest Sister had come to Kunlun, it must have been for something like that, but I guess I'm getting old now and I just couldn't remember. Of course, Kunlun was always welcoming. In fact, I'd rather ask you for a favor."

Then, Tian Feizi asked, lowering her voice.

"If it's not too much to ask, do you already knew which Movement it would be? I heard that Shaolin has the First Movement and Zhongnan has the Seventh Movement? Hmm, it's too much greed to want the Ninth Movement, but I'd be more than satisfied with the Fifth Movement."

"Ahaha, I'll try…"

Qing answered, scratching the back of her neck as if embarrassed.

\textit{Well, even if you say that to me…}

\textit{You should ask the Great Emperor about that. I can't just put them in any order I like.}

"Yes, that's a good thing. First, let's go see the cliff walls. No, I have to gather my disciples, so it'll take quite a while. The space was limited, and, well, if we're going to draw lots, it'll take some time. Come. Could you guide me to the Palseon Palace?"

When a master asks a disciple whether he will do something, it was not a confirmation process of asking whether he will do it or not, but a command, that is, do it.

Of course, it wasn't particularly difficult for the Borax people, and guiding guests was a great joy for the Kunlun Taoists, so of course they would do so.

Originally, the Kunlun wine was passed down to the Yeonghwan Taoist priests called Yeonghwan Palace.

But compared to the fact that the study of the uneducated was developing and its achievements were increasing?

Sorcery was extremely difficult to understand, and talent was crucial. Furthermore, since it essentially relies on the power of others, its popularity has gradually declined as it was not followed by personal training.

You can't force someone to study a technique they don't want to learn just to continue the tradition, and even if you do, there's no way you'll get good results.

Of course, the number of those three will inevitably decrease.

As a result, it was integrated with the Palseon Palace, which trains in alchemy, and the alchemy masters inherited and managed the records.

This was an easy-to-understand explanation from the emotional man with the booming voice, Bongsain.

Guided by the monk, we delve deeper into the rugged mountain terrain next to SamQinggung Palace, and the Palseonggung Palace appears beyond the Palseonmun Gate.

Although the magic itself has been largely lost to time, the Kunlun school of magic was said to be the best in Zhongyuan according to records from previous generations.

If I were here, I would surely know something about this grateful, yet strangely immune constitution of the blood poisoner.

So, Qing swallows his saliva and steps into the hall of Palseon Palace, where the scent of medicinal herbs fills the air.