\chapter{Journey to Kunlun (7)}

Of course, Emperor Mucheon did not turn his gaze away just because Qing was being treated unfairly.

Rather, wouldn't it be better to let out a deep sigh?

"What? What does that mean? Why do you look at people so pitifully—"

"Okay. There were three types of food in Kunlun."

After saying this, the Great Emperor Mucheon stands on the ground with his feet planted in a gesture that was completely without any trace of emotion.

The sword he had been sitting on swirled around Mucheon Daeje with a rather impressive trajectory, and at some point, it was gently wrapped around his hand.

It's cool though.

I've already heard it, so somehow.

Of course, Qing doesn't hold back what she wants to say.

"Did you practice that too? To look cool in front of your juniors?"

"Yeah. Just standing there, feeling a sense of weight, staring at them as if you know everything, your mouth shut, nodding or doing nothing. Thinking that anything could happen, you just pretend to be calm and watch, while internally calculating when you should step forward. Does that make you any kind of authority? You have to take care of your own authority. It's all the little touches of elegance that add up to great authority."

"You don't usually say things with your own mouth, do you?"

"Don't you see how those birds, floating proudly on the water, struggle beneath? Style was all about effort."

"I don't usually say things with my own mouth."

"Am I an ordinary person? And what have you been taking from what I've said so far? When someone speaks, you should at least pretend to listen. What's the use of having pierced ear holes? You pierced two of them. Why were you hiding my efforts as a flaw?"

"Huh, did you say that when you were alive?"

"then."

Some say that this senior was a man who spoke louder than words, but I don't think he was ever recorded as such a foul-mouthed, foul-mouthed grandfather.

Why do I think of the masters of the past who kept their mouths shut to uphold the dignity of their seniors?

I think it might have been right if I hadn't closed it.

"Enough. Enough with this boring chatter."

The Great Emperor Mucheon holds the sword firmly with both hands and twists his waist to pull the sword back.

Arms twisted to their limits, muscles bulging and bulging.

A foreshadowing of a mighty roar that was about to leap out—

"Three types of food. The master acts according to the situation."

The sword strike barely grazes the ground.

Passing by the steps of the footsteps, the exhilarating trajectory stretches toward the infinitely stretching sky.

A wonderful gesture of swinging one's entire body, which had been coiled up tightly, in one motion with all one's might.

It was a graceful, upward-facing herbivore.

In that appearance, Qing somehow saw a similar shape, ah, hitting this ball and putting it in the hole.

The seal claps its hands.

"Oh. Did you hit the ball?"

"What nonsense were you talking about? That's enough."

Anyway, it seems like he liked Qing's reaction.

It was MuQing or Mucheon Daeje who shows a cheerful smile even while interrupting the conversation.

"The power of the martial artists being comes from the earth, from the soles of the feet that stand firmly on it. This does not refer to warriors or the twisting currents of the body, but rather to a more primal law. It refers to the complete power of myself, my body."

The reason why it was rare to see a herbivore being used in Wulin was because the method was extremely inefficient.

All things in the world fall from the sky to the earth.

So, it was convenient and efficient to use the power from top to bottom when swinging the sword.

"If a man were to crush a rock, even a man with a hundred thousand pounds of strength would never be able to crush it. Instead of the rock breaking, wouldn't his feet lift off the ground and he'd have to hang on, supporting himself with his arms?"

This was a power that flows from above to below.

This was the limit of the expedient method of relying on the laws of the world for convenience.

No matter how much a warrior uses his mysterious skills to gain weight, he was ultimately bound by the weight of his own body and cannot remain whole.

"But if a person were to lift a rock, they could utilize the full force of ten thousand pounds. So long as the soles of their feet were firmly planted on the ground and their legs don't bend, they can unleash the full might of their body. Especially for a Strange Monk like you, who was so ignorant and brawny, this was even more true."

"Why do you always say such wonderful things when you're doing so well?"

"To stand upright with your feet firmly planted on the ground was in itself a violation of the will of Heaven. It was the natural order of all things in the world to fall from above. What do those animals look like?"

The beasts do not dare to resist the will of heaven, so they lower their bodies and crawl on all fours.

"But humans, and only humans, stand on two feet and stride with their heads held high. Therefore, humans can go wherever they want on their own. What's the point of being born? We have the inherent right to follow our hearts. That's why the most foolish of us all talk about fate and natural order."

Why do we, who were already defying heaven by our mere existence, talk about natural law and fate?

If it were our fate to die anyway after time passes, why bother being born and worrying about the heavens when we could just die early?

"So, the point is, keeping your feet firmly on the ground was the most important virtue for a human being. This was what everyone instinctively strives to achieve from birth."

Suddenly the world seems to stretch out far away.

The earth stretches out like countless ropes and touches the sky, and the sky flows down like falling water and blends with the earth.

"Have you seen those newborn babies struggling with all their might to get up? This was the very nature of people who long to stand on their own two feet and walk."

"Oh, you're not going to do the practical training this time?"

A world where the sky and the earth were united into one, a world of slick colors.

It feels like the vague and ambiguous Great Emperor Mucheon was smiling brightly.

"So, walk with all your might, young hemp. Where you stand was the center of the world and everything (Ipcheo-gae-jin).

and.

The Great Emperor Mucheon, who had been completely covered in watercolors, opened his mouth sharply, revealing his pure white teeth like freshly steamed tofu.

"But. A girl who can't even walk properly? What? Hwa-kyung? She's barely able to see the world and stand on her own. Her legs were shaking, like a newborn."

"Then let's cancel the practice. Ah. Ah."

But it was already too late, Qing's body was gripping the sword, his waist was turning, his arms were being pulled, and even before he had even swung the sword, he could already feel his muscles bulging.

"But this time, even if the muscles were damaged, the bones won't be damaged."

"Oh, was that because I'm an expert?"

"What were you talking about? Whether it's the peak or the scenery, it's all the same, three or five steps."

"Wasn't that fifty or a hundred steps?"

"Your level was exactly five, you idiot. If you were to change your drinking glass to a rice bowl, would it hold all the water from a cascading waterfall without breaking? Sure, it would hold a little more than before, but it's the same thing anyway."

"Hehe, then you can go easy on me."

"A beast will give it its all, even when facing a small creature. I've never once in my life shown any mercy. Unfortunately, the three-pronged attack was a test of one's own strength, so it doesn't produce enough damage to the bone."

As the danjeon boils, the internal energy rushes through the body in a rough, giggling flow, filling the entire body with energy and reaching saturation.

The Qing's internal energy has already surpassed the realm of the highest level and was incredibly powerful, so even the well-cultivated energy of the Reverse Realm Master cannot handle it.

Ah. Right. This. It was like this.

Why shouldn't I, why shouldn't I, shouldn't I come to see the cliff?

What glory do you expect from an old man like this?

As if I had reached the top of a crash-land amusement park ride in my hometown, all sorts of regrets came flooding in, and the scheduled time was—

Ugh. The terrible, rupturing pain of the veins and arteries throughout my body being torn apart.

It felt like hundreds of millions of ants were crawling into every blood vessel in my body, biting at it.

The blood vessels on Qing's beautiful face bulged, visually appealing to this terrible pain.

In a time that seems to have stopped completely in pain, only the annoying voice of MuQing or Mucheondae penetrates my ears.

"Okay, if possible, try to visit the Kongtong Sect next time. And don't even bother visiting Wudang Sect. You might really die."

And finally, the arms start to move.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As soon as he entered the cliff, the focus of the Thousand Flower Sword disappeared, and his blue eyes, which had lost their luster, stared blankly up at the cliff.

The Kunlun School's warriors were excited,

I stare intently at the Cheonhwa Sword with the feeling of a child waiting for his father to bring him something delicious.

Because they were the Kunlun faction's warriors who were already boasting among themselves about what the Jongnam faction's warriors were already boasting about.

What kind of martial arts did the great master Mucheon leave behind?

When we talk about our Kunlun, it must be the Yunlong Dapalsik, the exquisite divine skill of freely flying and releasing skills, as if clouds and dragons were playing in the sky.

So, isn't the wisdom of the Great Emperor Mucheon, who left behind after seeing that martial arts, a great skill like the Bungsae that rules the sky, truly like the master of heaven?

Then, a single word, that unique, piercing, beautiful voice, flows out of Heavenly Blossom Sword's mouth.

"Such a trick, such a mouth."

It's not that difficult. But why? Here?

It was a time when the Kunlun sect warriors exchanged glances, unable to speak for fear of disturbing others.

Suddenly, the Cheonhwa Sword begins to move, and the muscles bulge as the sword was pulled back as far as possible.

They were surprisingly vicious muscles, clearly developed and split like they were carved from stone.

Just as I was admiring him, the tip of the Heavenly Blossom Sword's sword grazed the floor.

A brilliant light that bursts forth like an explosion.

A sword strike that soars from the earth into the sky.

A brilliant stream of energy rises from below, cutting through space and rising into the sky.

It was the aurora of all colors that spreads from the earth to the sky.

A loud noise, as if the world were collapsing.

Dust rises and pieces of stone fly in all directions, isn't this the harmony of a man's sword collapsing and destroying a cliff?

The dust that had been thickly covering the world soon settled.

Because the cliff's debris was not smooth to begin with, it was bound to sink quickly.

The fallen Heavenly Blossom Sword appears.

The muscles of his entire body, which had been swollen and ugly as he lay on the floor, vibrated violently with a force that was clearly visible.

Full body muscle rally!

Heavenly Blossom Sword, stop overworking your muscles!

Severely torn muscles squeal in unison, sending a violent protest to their owner.

But the Kunlun warriors were not in the right state to pay attention to the Heavenly Flower Sword.

A sword's trajectory extending from underground to above ground, clearly engraved on the cliff!

It was a trace of climbing up a dozen or so steps and finally collapsing to the very top of the cliff.

The traces of the broken barrier rose up in a winding pattern.

If a dragon that had been crouching on the earth ascended, it would have left a trail like this, a magnificent sight. Here was evidence of a man's ascension achieved with a sword.

It was a great teaching that the Great Emperor Mucheon wanted to leave to his disciples in Kunlun.

Before you look up to the sky, know that you were standing on the earth.

Also, stand firm on your feet and stand firm on the ground.

Then, standing in place, you will be able to summon the dragon and ascend to heaven.

A lot of work, a lot of openings.

Being the master of oneself wherever one is.

Because the place where you stand was the center of the world and the truth.

And in the middle of it all, Qing barely opened his mouth.

"Ugh, over there, huh, huh, gasp, over there, buy, uh, man, save me……"