\chapter{Journey to Kunlun (4)}

The building we arrived at after being guided by the monk was Yeonghwanjeon, located in the center of Palseon Palace.

Although the Kunlun Yeonghwan Dao lineage was virtually extinct, its records were extremely useful for alchemy and were secretly interesting.

As such, many of the Taoists on the platform have taken up karma as a hobby, and among them, the Taoist named Danlun Zhenren was said to be the most thorough.

As expected, the Danlun Zhenren was already seated inside the Yeonghwanjeon Hall, transcribing the old book and binding it anew.

Since it was a private affair, the group was already resting in the guest room, and Bongsa-in also left the room to take a bath and cleanse himself before seeing the cliff.

Then I thought to myself, "Single-eyed Zhenren, a middle-aged man with two eyes of different sizes, can't possibly be a single-eyed Zhenren with only one eye?"

Of course, it was unlikely that this will happen, as the greatest disciple of the Kunlun sect was Dan Ja Bae Hangryeol.

Even when Qing greets him, he waves his hand.

When I asked if I could sit across from him, he nodded.

Even after sitting down, he just presses down on the book and learns the binding, so he was extremely blunt.

Qing, let's start with a trivial story.

"Well, what kind of book was that?"

"It's a book of sorcery called "The Book of the West Palace of Kunlun." As a Taoist, you'd know. Kunlun Mountain, the mountain where immortals reside. The West Palace was the residence of the Queen Mother of the West, so this is a book of sorcery on borrowing power."

"Oh, a sorcery book."

A very old memory suddenly flashes through my mind.

Now that I think about it, I think I saw it in the Taepyeong Magic Book and the article posted by Strategy Editor.

If you touch this, what will come out?

"Can I take a look?"

"Slowly. I've finished copying, but the original manuscript will always be valuable."

Qing cautiously reaches out to him.

But it doesn't seem like the Martial Art Window is glowing, um. This isn't it.

Qing, who has lost interest, talks roughly.

"Then it's a precious book. I don't think it should be carelessly touched."

"Yeah. That's right."

After Danlun Jinyin carefully placed the original Kunlun Seogungpyeon in a small book storage box, he closed the lid and applied something brown from the soup bowl to seal it tightly.

He felt a little sorry for Qing.

Hmm. I thought it was Jo Qing.

I guess it wasn't meant for dipping snacks.

As Qing looked down at the sealing glue with a look of longing, the Danlun Zhenren, who had meticulously finished storing it, finally looked at Qing.

"So, what did you come to ask, Sodojang?"

"Ah. Yes. I was wondering if you might know me as a blood poisoner."

"I don't know."

It was an immediate answer without a single moment of hesitation.

What, don't you usually pretend to think a little even when you can't think of anything?

When Qing made a dumbfounded expression, Danlun Zhenren shook his head slightly.

"Magic was incredibly ambiguous. Even within the same technique, it varies by region and era, and the very words themselves carry a certain power, so there were even twisted and derived techniques. So, you're asking what kind of technique it was based solely on its name? Unless you have that kind of tradition, you can't possibly know. So, if you keep asking around like that, you'll have to find someone in Zhongyuan who actually passed down the secret technique, and you'll never find them."

What's going on? You've become more talkative? Isn't that a good sign?

"Then?"

"Explain what the blood poisoner is. Only then can we find similar concepts in our history, compare them, and deduce their origins. So, what was this blood poisoner? Oh. Wait. Don't answer. Let me think for a moment. Blood poison, dead blood. Poison. Here, blood poison, poison, yes, decay, along with poison, and corruption. If we interpret it as decay, it's a metaphor for a corpse. But I didn't specifically say "corpse," but "poison," "in," or "person." It's natural for a corpse to have dead blood flowing, so it's not natural. So, it's a person who was like a corpse, or a living person with dead blood flowing, something like that. What do you think?"

"Oh, right. I think so."

"Then, blood poisoning, dead blood. Rotten blood. Blood that died in alcohol. Hmm. Hmm. I don't know. So, what was this blood poisoning thing?"

"Hmm. Not only was it non-toxic, it doesn't cause any harmful effects on the body—"

"Ah! So, dead blood. That makes sense. Yes. A knight. A living corpse. He's already dead."

"Do you know something-"

Qing, unable to hide his delight, tried to urge him on, but Danlun simply raised his hand to silence him.

"Wait. Right. I get it. The origin ceremony of the Hwanhonjageon. The Great Taebalbonjesa Record. Right. I see. That's it. So that's it. I see. Now I get it."

If you know something, could you please share it?

Why do you keep telling me this and I still don't know?

It was a time when Qing felt suffocated, as if he had swallowed ten sweet potatoes, no, ten wasn't enough to block Qing's throat, so he felt as if he had swallowed a thousand.

The single-minded Taoist priest suddenly stood up from his seat and disappeared into the countless desks with hurried steps.

Qing was looking around with nothing to do, and then he took a sip of the brown liquid used for sealing and tasted it. Oh, bitter. This was some kind of tree sap.

And then, after wandering around for no reason, I lie down on the desk with my heavy chest resting on my chin.

If you get caught by the master, it's a posture that immediately projects the power of nuclear weapons, but how can you do something so comfortable like this?

Master, you should honestly understand this. You, of all people, can fully empathize with this.

For some reason, I dipped the tree sap in it again and slurped it into my mouth.

Hmm. This tree smells fishy. It's really not tasty.

As expected, it's not something people eat. I used to eat tree bark a lot.

Those damn kids, they beat people up by peeling the bark off a tree and eating it instead of letting it die.

And then he pointed and pointed, pointed and pointed.

Hmm, as expected, as expected, it's tasteless. This bitterness, that unbearable grassy smell, Hmm, it really was tasteless.

If someone saw and heard it, they would ask why I keep eating it and frowning when it doesn't taste good.

Then, at the sound of footsteps coming back, Qing straightened her posture as if nothing had happened.

The Taoist monk Danlun, who had returned with several books tucked under his arm, sat down and looked at the slightly lowered water level in the bucket, making a puzzled expression.

Qing pretended not to know and opened her mouth.

"Did you find the record?"

"Yes. I found it. It's a truly sinister and evil name, a blood poisoner. I couldn't bear to associate the two. It's the Taeje of Hwanhonjageon. Hwanhon means to return the soul, and Jageon means to walk on one's own. Furthermore, Taeje refers to the greatest of all sacrifices, a great sacrifice that brings the dead back to life."

"A resurrection ceremony?"

"Yeah. Look here."

The single-minded Taoist priest picks up the book and turns it over.

When the Qing came in, he was working on copying an old book, but it seemed like it was already bound and was still a new book with a nice finish, so he was handling it roughly.

And then unfold one part-

What? Isn't this the kind of atmosphere you usually show to me?

Why do you put it in front of you and only look at yourself?

"This was a ritual to ask the Guryongtaemyoguisangeummo to return the soul of the deceased. This ritual requires the sincerity of the individual to impress the master of the West Palace. Therefore, even a single tainted hair of evil spirit could lead to a devastating divine punishment. It was a very dangerous ritual…"

However, humans were made up of soul and body, spirit (soul) and flesh (body).

Even if the Queen Mother of the West returns the soul out of mercy, if the body was already dead, any sacrifice was useless.

So, the first thing was to keep the body alive from dying after the soul leaves it.

A body that has lost its soul does not breathe on its own, so the living must take care of it with devotion and breathe life into it three hundred times a day.

Also, as vital energy was lost, it must be continuously replenished with elixirs.

Since you have to hold your breath for forty-nine days, you naturally have to take care of your diet as well.

"Hmm? Isn't that a little odd? The Queen Mother of the West was the ruler of the West Palace, a Taoist cult from before the Zhou Dynasty. But isn't the forty-nine-day journey to the afterlife a long time ago?"

Before the law took hold in Zhongyuan, the place where the dead went was the West Palace, the Jade Peak of Kunlun Mountain.

However, as Buddhism took hold in Zhongyuan and Taoism accepted the Buddhist worldview and readjusted the ranks of the immortals, the Buddhist underworld was relegated to the lower ranks of the celestial world's death handlers, that is, the lower ranks.

And the Queen Mother of the West, who originally ruled over death, achieved a tremendous rise in status and became the leader of the female Taoist immortals who oversaw all of the immortals.

Then, the bluntness of the single-minded Taoist priest subsides a little.

"Yeah. For a young person like me, you seem to have studied the original text quite a bit. The Queen Mother of the West from Cheonryeo-o-jan seems completely unknown to young people these days."

Well, that's because a club was the most powerful learning motivator.

"But that's the way sorcery is. It's a mess, a jumble of things mixed together to suit my taste. Anyway, what kind of sincerity was it that can keep someone already dead alive for forty-nine days through human effort? Even the Queen Mother of the West would be truly impressed."

And on the forty-eighth day, a great sacrifice was held to ask for the soul to return. This sacrifice must be completed on the forty-ninth day, exactly at the time of the deceased's death.

Even if it was a little early, it was still under the jurisdiction of King Yeomra, so even the Queen Mother of the West cannot take the soul out.

If you were even a little late, you will have already passed through the gate of reincarnation, lost all your memories, and will be living the life after that.

So when the sacrifice was successfully completed, the dead person will rise again and walk on his own.

"But even if the dead, the knight, speaks, thinks, and walks, he was ultimately dead. The dead do not die again, and the memories of the living cease at death. Therefore, the knight was immortal, never aging, and never dying."

"Huh? Immortality?"

"Of course, it's not true immortality. There's even a record of it here."

The dead cannot die.

But you can kill the dead.

This was the punishment of taking out a dead person and killing him again.

"If what you say was true, then the blood poisoner seems to have very similar characteristics to the knight. Poison doesn't work, has no harmful effects, and was useless on the dead. The only way to kill someone already dead was to cut them down."

"Well, then, could it be that another spirit has taken possession of the body?"

Then, the Taoist monk Danlun snapped his finger!

"Ah. Indeed. So that's why you're a bloodthirsty poisoner. It felt like a vicious and horrifying name. Reviving the dead was akin to defying heaven. Still, it's a realm of human compassion, rooted in order, love, and longing. Therefore, the Queen Mother of the West, moved by your kindness, will return your soul to you."

The single-minded Taoist nods his head.

"But if what you say was true, then that's a different story. Why would someone infuse someone else's soul into an immortal Strange Monk? I can think of two reasons."

One was that the one who becomes the master of the spirits seeks immortality and attempts to achieve immortality through his own death.

Another was to breathe in a spirit that can control an immortal Strange Monk to use it.

Either way, the intention was utterly evil, so evil magic cannot work unless it has an evil name.

"This was truly a horrific sorcery. Where on earth have you seen such a monstrous thing? If such a thing exists, it must be a Strange Monk Wulin cannot tolerate."

A pang of pain in my heart. A pain as if cut by a knife.

Qing forced a smile to hide her sinking heart and answered.

"Hmm. The shamans."

"Ah. Those traitors to the spirit-reincarnation technique. Then they could easily do it. Originally, jiangshi was the fundamental technique of the spirit-reincarnation shamans, a benevolent endeavor aimed at returning the corpse to its family. However, they gradually developed selfish desires, using the corpse as their own. That's why they were specifically called jiangshi shamans and were now guarded against them."

"Ah. Right. About the zombies too-"

"But it's truly a terrifying sorcery. Originally, the word "Honbaek" meant "Hon" (魂) and "Baek" (魄), and the character that goes into both was "Gwi" (鬼). This "Gwi" refers to the soul, while the human soul and Baek were fundamentally the same, with the only difference being that the soul belongs to heaven and Baek belongs to the earth."

I've been thinking about this for a while now, but he's truly a single-minded Taoist who lives as he pleases.

"Therefore, it was impossible to transform the truth engraved in words into a spirit. Therefore, it was impossible for a soul to inhabit a human body unless it was one's own."

But wasn't Qing already living with a mental parasite somewhere inside her?

The guy named Cheonmahon did it too, but I wonder if it's not possible to do something different.

"Is it completely impossible?"

"Nothing was impossible in magic. However, a magician capable of altering the true meaning engraved in the text would be a half-sage, a martial artist at the level of life and death. However, throughout history, only two magicians have achieved this: the True Man of Wuji and the True Man of Zuozi."

"You guys were really old."

"Since then, martial arts have developed. Naturally, sorcery has declined. Therefore, it's impossible for a sorcerer to achieve the highest level of enlightenment in this era, and therefore impossible."

But isn't Qing already inside this body?

To say it's impossible, ah, then suddenly the Empress Mama's words come to mind.

-I didn't entrust you to the witches of Heaven, I didn't trust them.

"Ah! Heaven! What about the maidens of Heaven?"

"You said you were a shaman? You wouldn't know the circumstances of my Heavenly Kingdom. Well, a Heavenly Kingdom shaman might be possible. But if a shaman of that caliber exists, there's no reason to go against the natural order and take on Strange Monks as subordinates."

There was no reason for someone who was already capable of shaking the world with natural disasters, such as shaking the earth, causing floods, and creating droughts, to go against the will of heaven and create something like a living corpse.

"Huh. You could make it."

"Did the Great Emperor Mucheon, with his martial arts prowess, write a letter urging suicide? No, he simply went and cut himself with his sword. Would you, when you're killing an enemy, write a letter urging suicide instead of a sword? Sir, if what you say was true, the blood poisoner was that letter. Even if it's immortal, why bother when it can be killed with human strength?"

"Well, I don't know. Maybe he's just bored? Maybe he's just bragging about being able to do something like this?"

"That could be true."

Anyway, it was a big gain.

Because I knew that the existence of Qing could be explained by the methods of this primitive ancient martial arts world.

Not some strange intervention of some cosmic being or part of some woven virtual world.

That alone was a great relief and puts my mind at ease.

And. Um.

Am I not aging? Hmm, no, I guess not?

Qing couldn't feel the aging process for a while.

It's hard to find a mirror in this neighborhood, and even if there were mirrors everywhere, it's hard for you to notice the changes in your face.

Besides, originally masters even age slowly, so, hey, no way.