\chapter{Journey to Kunlun (9)}

Cheonbija smiles brightly and answers.

"It's so bitter and its energy was so harsh that it's dangerous, so only a master of the Hwagyeong class can eat it. It's just fate that a master has appeared at a time when no one else was willing to give it to you."

"I did write. I do. Actually, I still do."

Then, Cheonbija smiles brightly and holds out a large piece of candy as if she had prepared it.

Qing happily accepts it and quickly puts it in her mouth.

The aroma, taste, and sweetness of the sour hawthorn berries flood in, and I feel like I can finally live.

If you eat something bitter and something sweet, it becomes twice as sweet.

In an instant, both eyes take on the shape of a rainbow, and a double rainbow blooms over her pretty face.

Cheonbija looks at Qing's cheeks, which were bulging with candy, and bursts into a cheerful laugh with an expression like watching her granddaughter's antics.

"Even when I was young, I swallowed it whole. was this the punishment of hell? Even poison wouldn't be this bitter. was the Master going to take his disciple away now? The bitter, painful taste still lingers in my mouth."

The horse was too rough, isn't that the technique for such times, the true technique, the art of the master guiding the energy?

So, the claim that there was no one to give it to was actually a blatant lie.

Of course, if you were a disciple of Kunlun, you might ask, "There were many other medicines, so why do you tell me to take that terrible one?"

The words that follow are, 'Oh, of course I'm not saying I won't eat it, please give it to me quickly,' and it's a potion that you swallow quickly in case you change your mind.

In the first place, there were more than a few people in the world who would eat an elixir and die if it meant dying.

If they said, "Seowangcheondodan was for sale right now!", the entire martial arts world, even this remote mountainous countryside, would be teeming with people carrying gold nuggets.

Of course, it was not a pure favor, but a gift with some purpose mixed in.

Of course, since the chiefs were suspicious, the best martial arts masters will come to support them. Then, wouldn't Senior Ximen Surin come too?

They say he cherishes his disciples so much that his past infamy pales in comparison, but what if he heard that after seeing the cliff and collapsing, his entire body was covered in bruises and swelled up?

How can I handle that temper?

So, if I told you that I had fed you one pill of the Seowangcheondodan, wouldn't you nod and say that it would be enough to tear your muscles?

That is, it was a kind of lubricant for the relationship.

The network of relationships between the political faction that the Sapa and Ronin were so jealous of, was this how their minds work?

In addition, I also have a secret wish.

"Yes, Sosa-mae, haven't you personally wielded the herbal formula? From what I can see, it's a skill that embodies the highest level of perfection and chastity. I wonder what Senior Emperor Mucheon felt when he observed Kunlun's martial arts and wrote about it. I'm still lacking in my realm, so I can't fathom the meaning behind it."

"Oh. That's it. So, um, um."

Qing took a moment to choose his words.

It wasn't that difficult since I had already tried the first draft and read the image.

"Konlun originally referred to the celestial realm where immortals reside. Isn't the Kunlun Mountain on Earth simply a name given by people in the past, who were awed by the rugged mountain range? Therefore, the Taoist priests of the Kunlun sect say that if you establish a Taoist center in your heart and believe that it was Kunlun Mountain, you will be able to stand anywhere and find your center."

How to make a lot of money.

The saying that we should be the master of wherever we reach means that we should proudly stand with our shoulders back and make our heart, our center, our home, independent of that place.

Then, open your mouth.

No matter where you stand, you will not be shaken and will soon be able to realize that you were standing at the center of the world and become the truth.

When it comes to truth, one's own will was true, and one does not doubt it when comparing it to the world, because it was one's own truth.

But was that okay?

To sum it up, it's kind of like that.

Anyway, I live my life, so I do whatever I want!

I understand that I am the center of the world, but that doesn't mean I should live as I please and not seek the world's understanding.

If it works out well, you're just a lone wolf, and if it doesn't work out, you're just born an antisocial criminal.

Grandfather Mucheon Daeje, was this correct?

Aren't you living alone in this world?

We live in a world where we all live together, so how can I just swing my dick around however I want? That won't do.

Hmm. When I look at this old man, I feel like he doesn't really fit with me.

If the Great Emperor Mucheon were here, he would beat his chest and slap Qingdo, saying, "Oh my, this really was a dog-like, stuffy bitch. Her head was pretty, but she's useless for anything other than decoration."

However, Emperor Mucheon was no longer a person.

"Huh. So, the Great Emperor Mucheon wasn't satisfied with Kunlun's techniques. He even scolded me sternly, saying, 'How can you fly when you don't even know how to stand properly?'"

"oh."

I tried to wrap it up in a way that would make it look like a fool who could immediately see through its true meaning.

Of course, Cheonbija did not choose the long-term position by lottery, so even though his realm was only Hwagyeong, he was an old Taoist who had studied all his life.

Cheonbija smiles brightly at Qing's transparent expression as if it's okay.

"It's okay. I haven't been able to reach the far-off realm of Kunlun for a long time, so I wondered if, after my move, the land wouldn't be as rugged as the Kunlun Mountains, making it difficult for me to achieve greatness."

A faraway realm.

The word 'Adeokhada' was written as 'Hyeon', which means 'sword', and it means 'realization of the real world'.

"Perhaps, since moving, I've been unable to stay on Kunlun Mountain, and it seems I've unconsciously become a rock in my heart, blocking it with my mind. Kunlun didn't originally exist, so wherever Kunlun's disciples are, Kunlun Mountain was where they are. Now that I've finally grasped the edge of enlightenment, I should call my brothers and discuss it with them."

Even if he was an old warrior, would his passion for the realm have waned, as his eyes sparkled with the light of a thousand stars?

It's just that the spark was extinguished and hidden because it was far and difficult, but the desire of the martial artists always rises like a flame.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Qing was first brought in on a stretcher made of the kasaya of Kunlun Taoist monks, he was covered in crimson bruises all over his body.

When I woke up one day, it was all swollen and purple, because the color of the bruise kept changing depending on the details.

On the first day, no matter what I did, I was in pain and my torn muscles were protesting in pain, telling me to just chill out, so I had no choice but to lie down quietly.

That doesn't mean it's uncomfortable.

Wouldn't Qing have the world's best water gun expert, Master Jiang Pohui, by his side?

It's more convenient for eating and drinking with my hands than with my own, so Jian Buxi, who knows her well, puts the side dishes and snacks she wants in her mouth without her having to ask.

Compared to that, Gunyeong only puts delicious food in her mouth.

Of course, it's admirable that he wants to give me something delicious.

But still, porridge porridge tang tang porridge porridge tang was too much. Give me the meat, give me the meat.

On the one hand, it was the most comfortable vehicle and provides unwavering comfort, and on the other hand, it provides mental healing with its swaying comfort.

Petting an animal was the best therapy?

No, there's something better than that. Tsk tsk.

I don't know this.

And above all, as always in the Demonic Cult, he was an absolute master in the art of bathing, unrivaled by anyone in the world.

Gently rubbing the body of Qing one, but not too gently, with just the right amount of pressure, it was refreshing and like a massage on the torn muscles, a perfect balance that suited this body condition that no one else could imitate.

Qing, without realizing it, was tired and slumped over.

Jian Buxi, who was wiping Qing with a fine cloth, suddenly bursts into laughter.

"Hehehe."

"What? Why were you laughing?"

"Sorry. But it's funny how only your chest was white."

Well, that's because there were no muscles in the chest either.

Qing was a character who experiences the truth that it was dark under the lamp at every moment.

So even if I look down, I don't know for sure.

Well, if you think about it, it might be funny.

The sight of Qing was the source of Jian Buxi's laughter, and she burst out in innocent laughter the whole time.

Still, as the days pass, Jian Buxi's laughter gradually decreases in volume.

Well, the body changes from purple to navy blue.

The color changes from navy blue to turquoise, then green, and then gradually turns yellow.

Because he was unable to move, he only washed himself on the bed and even changed his position to the guest bathroom. After ten days, except for his white face and white chest, his skin was as yellow as those southern barbarians, and he looked as if he had been covered in a lot of dust.

So, on the tenth day. Breakfast.

A sumptuous breakfast table prepared by the Kunlun School Taoist priests who learned of Qing's appetite.

It was on a scale that couldn't be called a breakfast, but it was closer to a banquet.

In front of the magnificently prepared banquet table, Qing was a girl who chewed the food that was constantly being put in her mouth without lifting a finger.

Then he suddenly says:

"Should we go see Qinghai Lake? I'm almost better now. Qinghai Lake was just a lake, after all. But Chajap Lake, Chajap Lake. The scenery was breathtaking. Wow, I've always wanted to see something like that."

When I say past, I mean before I entered Wulin.

If you come to Qinghai, you can't say you've been there without seeing Chajabho and Qingongjigyeong.

It was a famous place that the sick person told me about when he asked if there was anything to see nearby.

After hearing the explanation of why it was like that, I realized, "Oh my gosh, you have to see this."

That was a sight I had wanted to see before, even before I entered Wulin.

For reference, it was said that when the shaman saw Qing lying down, he burst into tears with bruises all over his exposed neck, back of his hands, and wrists.

I just have bruises all over my body.

It was said that the tears were flowing so quietly that anyone who saw them would think they had a fatal disease.

This was why it was called the Jade Sword and the Tear Swordsman for no reason.

"You think you're all better now, looking like that? Can't you even lift a pair of chopsticks?"

Paengdaesan looks dumbfounded.

Well, all you do all day was lie down and sleep or lie down and talk, so where were you going?

"Huh? It's not that I can't hear it, it's that I don't want to hear it."

If the bruise has turned yellow, it means it has already healed, and there was no pain unless you press hard on the affected area.

Even so, why do you have to endure extreme treatment from your sisters, who do not lift a finger to eat, move, or even bathe you?

Yeah, it's comfortable.

"Do you usually act so casually just because it's convenient?"

"Huh? No? What do you mean, the truth? You're giving this incompetent brother-in-law and this very, very incompetent Iri the opportunity to hold the great Cheonhwa Sword? Right?"

"No." "Yeah."

Opinions on the left and right were diametrically opposed.

What was it? Left arm, left ear rebellion?

"What, was this why you don't want to take up the mantle of the great Transcendent Flower Sutra, Chojo Flower Sutra, Cheonhwa Sword?"

"No. I want to come in."

"No, no. This ride was just not comfortable. Don't you think they're being too considerate of their passengers?"

"No, no."

"No. I'm abandoning the old carriage and taking the golden carriage. I'll only ride in the rare one."

"Hmph."

It was a simple way to suppress rebellion.

Look at this guy trying to be cute again.

I kept letting her show me her cute side, and it was completely automatic.

But how dare you deny me the honor of serving this great and mighty Heavenly Blossom Sword, who was so great that even wounds heal three times faster, and who deserves to be called Heavenly Blossom Sword, three times over.

Even if you throw away your own fortune, it was still a waste of money.

It was a question that made me understand Amukhaprap's feelings once again.

Receiving alms was a virtue, and yes, providing opportunities like this was also a virtue.

Why would I ride around with my strong legs for no reason just because I like something?

Of course I ride it because it's comfortable. Wouldn't it be comfortable to move around while lying down?

"It's not like you usually ride in front of people."

"Well, that's how most people are. But Yi-mei isn't a normal person, is she? Why don't we ride together as a family? Right?"

"Yeah. Yeah. That's right."

At that, Paengdaesan sighed deeply.

Qing was shameless in the first place, but he's going crazy because those around her encouraged her behavior.

Anyway.

Chaka Lake's tourist group was decided.