\chapter{Journey to Kunlun (8)}

As MuQing or Mucheon Daeje said, if the person using it was purple, even if he uses a third-rate martial art, it was no different from a divine art.

In that sense, it can be said that all of the martial arts that Qing currently possesses have been upgraded to divine arts.

Well, I like purple, but I didn't want to become purple.

Unintentionally, Qing became a purple human.

My skin was all swollen and purple.

Even the muscles under the arms of the Minoru Demonic Power's semi-indestructible diamond were swollen and bruised with a purple hue.

That's because Dokgo Gugeom Samchosik Sucheojakju overworked and squeezed every muscle in his body beyond his limit.

Even if it was a small number, there was no other way to defend against the muscles being torn apart from within.

He didn't use his facial muscles to swing the sword, so his face was still alive.

And the fingers were white too.

Surprisingly, this was probably because there were no muscles in the fingers.

"You said you were going to see the cliff wall. Did you fight the cliff wall?"

Peng Daesan Mountain looks down at Qing sky, with Xue-i-ri and Jian Buxi on either side, and emits a low-frequency, deep voice.

"Well, it's similar. Haven't you seen the cliff wall? The baby dragon next to the big dragon was mine? It's because I lack internal energy. Otherwise, the cliff and everything would have collapsed and we would have all been wiped out."

I don't know at what point in the valley where I was moving like a cliff, I started having a conversation with the swearing old man.

Two dragons were seen as they were carried away, their muscles torn and all their affected parts trembling.

The Qingdo Sword also has a magnificent dragon carved from the ground to the sky, but it looks completely out of place because there was another huge dragon next to it.

It was a cliff wall carved by the Great Emperor Mucheon (the real one).

It's a demonstration of Qing martial arts. Only those who drew lots were able to see it, but if you compare the newly engraved sword marks with the existing ones, you should just make time to go see it.

I've already seen Pyeongdaesan and Xue-iri, and Gyeonpo-hee was only interested in taking care of Qing, not in those scars.

The Kunlun sect members were all lining up to watch, waiting for their turn.

"Huh. I thought I was finally able to walk around, but now I'm sick again."

"Hey, it's not a serious injury, it'll get better in ten days."

It wasn't like the muscle was severed, just half of a bunch of hairs were torn off.

Since the muscles were torn like that, it was actually a serious injury.

But by Qing standards?

What's the big deal about a few torn muscles and ligaments?

If the frame was intact and there were no torn parts, it will get better if you just lie down and rest.

"I heard that it could take longer than a month, maybe two weeks."

"Hey, I know my own body. What do the council members know? They're the council members."

"……?"

If a normal person were to say that, it would be something a bitch who would ruin her own life would say.

It was a reckless remark that would have been fortunate enough to only harm himself, and would have also caused trouble for many people around him.

But it's different when Qing says it.

Because Qingdo was a respectable female doctor.

In addition, the knowledge that he has gained from countless injuries was that Qing recovers three times faster than other people.

Details that can be extended from one month to up to two weeks. Although it was a medium-term injury of between five and eight weeks based on the Qing Dynasty's hometown.

What if we reduce that by a third?

It takes from ten days to at most two weeks, and unlike bones, muscles gradually reattach, so it takes that long to completely heal.

If you paint roughly, you'll be able to walk around in about seven to ten days.

You'll have to endure muscle pain all over your body, but it's not physically demanding, right?

So, Qingdo was a leisurely place.

I was planning to eat a delicious meal and get some good rest on a nice bed at Kunlun.

Actually, I think it would be nice to go home with the best support authority, Yi-mei, in my arms.

However, Kunlun's position also had to be considered.

How can you wave goodbye to a guest whose entire body was swollen and bright purple with muscle ruptures?

Since the Divine Maiden Sect was my house, I was able to somehow get permission by being stubborn.

But it was not something I could do to just leave for a mere ten days while losing face in someone else's house, Kunlun.

And I have something to tell you, Jang Moon-in-

-Hmm, Hmm. were there any minors?

It was frightening to think of the voice of a thousand people coming from outside the door, looking for Qing.

Usually, when a long-distance visitor came to visit, the disciples would arrive first and inform them of the visit and the time.

And even after arriving, it was normal for the disciple to appear first and announce that the elder was coming soon.

It was not only because the elders of Wulin were authoritative figures, but also because it was a protocol that those representing a group must naturally follow.

But you just come and ask how I am doing?

Whether it's an unofficial visit or one with as much intimacy as the members themselves.

Even if he was a long-time sect member, when he goes to see the disciples of that sect, wouldn't he just go and have a quick look, say a few words of wisdom, and have a meal together?

Xue-i-ri and Jian Buxi get up from the beds on the left and right with regretful expressions and move to the chairs.

Qingdo, ugh, as I raised my upper body, I felt a pain as if a hot iron needle was stabbing me.

Shoulders thump, sides thump, chest and abs thump thump thump thump. Ugh, save the Cheonhwa Sword.

"No, no, don't get up. Just lie there."

"Hey, how could that be? It's not serious enough to show you how I'm lying down, Jang Moon Jin."

"How can you say such beautiful things?"

Honey drips from the eyes of the thousand-year-old.

"You've come this far."

"Would you like to call my sick child? Yes, you too. It's truly wonderful to see such loyalty between friends. Oh my, your neck was so blue, and your hands too. were you feeling better? At least your face was bright, which puts me at ease a little."

"It's not that serious, it's just a little noisy. You don't have to worry too much."

"How could I not be worried? Here. I brought you some good medicine. Take it, invigorate yourself, and take care of yourself."

As he said this, Cheonbija opened a wooden box and held it out.

As soon as I opened it, a fragrant medicinal scent filled the room, and I could tell just by smelling the thumb-sized handan placed on the red silk that it was no ordinary item.

"Oh, isn't this a precious item?"

"You were indeed precious. Kunlun's elixir was the greatest art in Zhongyuan, so there were already plenty of even more precious ones. Furthermore, even I, a disciple of the highest order, cannot carelessly use such precious elixirs. So, hurry and eat. You need to take care of yourself first."

Still, I didn't say it wasn't a valuable item.

It was only a little bit like a cold, so I felt it was a waste to take the precious elixir, and even if I took it, my internal energy wouldn't increase much, so I was about to refuse.

A thought that suddenly crosses my mind.

Now, my internal energy was so great that I have transcended the realm of the supernatural, the supernatural realm of the supernatural, but when I reach the realm of the supernatural, I can no longer use the expression "transcendence."

Is that okay?

If you take away transcendence from me, what's left?

A fake martial artist who just uses his dirty brainwashing to master martial arts?

How can you achieve the same level of skill and power by using such convenient yet despicable methods?

That can't be possible.

If it were a martial art learned through some shady means, then the Cheonhwa Sword would have to be a transcendent being far greater than the realm.

So, Heavenly Blossom Sword wants to transcend.

"Well, then I will eat it with gratitude."

This was not the time to be complacent and think that what difference will be made if you increase your internal energy a little more like before.

Qingyi Wow, she shoves a large pill into her mouth.

If a large bead the size of a thumb was placed on the tongue, won't it just melt away and come loose on its own?

Just this alone tells you that it was a precious item.

And the explosive medicinal scent that seemed to fill every empty space in my head, like chewing on a mushroom.

And the melted Hwandan filled my mouth, and the taste was, oh my, bitter, bitter, what was this, ugh, bitter, save the Heavenly Blossom Sword.

Qing, who often ate sotae during his beggar days.

The pine tree was so bitter that even when people eat it, everyone just laughs and watches, and they don't use clubs like when they eat other trees.

Isn't that bitterness that's hard to bear?

It's not that this isn't valuable, but it's so bitter that no one eats it, so I wonder if they gave it away to get rid of the remaining bad stock.

Qing's expression was very arrogant, but he tried to force a smile to look good in front of the person who gave him the gift, but instead, his face became even more grotesquely distorted by the veins that had inevitably popped out.

At that, the idiot bursts into laughter.

"Seowangcheondodan, what's the use? Aren't medicines that were good for the body bitter? If you're going to be that picky, then it's the best medicine in the world."

The bitter pill, which had been swallowed with difficulty in the melted water, still had a bitter, stinging, and numb mouth, and a sad expression appeared on his face.

I didn't notice the shocked expressions on the faces of my two friends, Peng Daesan and Xue-i-ri.

No matter what anyone says, the most famous elixir in the world was Shaolin's Daehwandan.

But if you were to choose the most famous sect of alchemy in the world, it would of course be the Kunlun sect.

In the first place, wasn't the Queen Mother of the West, the master of Kunlun, the foremost of the immortals, the one who created the elixir of immortality as her masterpiece?

The Kunlun School's alchemy, which continues that lineage, was considered the best in the world, and was so precious that the Yeong-Hwan Hall was located in the deepest and safest part of the school.

Even in that Kunlun Mountain, there was a natural habitat of the miraculous plant called Bandowon, and even after moving, the Kunlun Sect was constantly receiving elixirs as elders would come to harvest them once every ten years or so.

How could the Kunlun sect, which was born in a remote area with no people and had difficulty recruiting disciples, have lasted for so long?

It was a history of maintaining the realm by forcefully raising it by using elixirs to compensate for the inevitable geographical limitations of the disciples' lack of talent and delays in initiation.

Of course, Jian Buxi doesn't know anything about elixirs, so she just thinks it's a good medicine.

Qing was just out of his mind from extreme bitterness.

It's so bitter, so bitter that soju will become sweeter in the future. Seriously, it's so bitter…

"Wow, this was really useful……."

But that was only for a moment. Energy exploded from within, lava-like heat rising upwards, while ice-like cold seeped down.

Qing immediately closes his eyes and directs his energy.

The hot yang energy pushes downwards and upwards, and the yin energy pulls upwards and upwards.

Then, since it was a yang-seung-yin-gang, hot things naturally move upward and cold things move downward, after one round, they were forced to change places again.

Every time it turns like that, the weak energy passes through the center of the flow, the dantian.

All kinds of energy residing in the dantian were running wild and excited.

I bury my head in the powerful flow of the weak energy passing through my dantian, and I am busy swallowing it greedily, biting it with my teeth.

Wow, it's delicious, it's so delicious, the gods were so excited that they can't seem to hide their admiration.

The ball was swollen to the brim like a squirrel stuffed with its balls, and its mouth, which was chewing on the balls, was gaping open in happiness.

The eyes sparkle like a sea of stars in the night sky.

A delicacy that makes your ears perk up and move because of its delicious taste.

It's a huge feast, a feast where everyone was eating and enjoying themselves to the fullest.

So when Qing opened her eyes.

Oh, what was it,

I blinked my eyes at the amount of internal energy that had grown considerably.

Well, the absorption rate of the elixir was almost 100%, and it was close to complete absorption, so it was easy to absorb the elixir.

But what was this?

I've tried Daehwandan too, but it seems to have half as much energy.

After all, Daehwandan was the ultimate health tonic that even commoners who don't know martial arts can eat, and it controls both energy and blood.

It was considered the best spirit sword in the world because it was safe enough to be eaten even when your body was a rag and you were about to die, but if you only consider the potency, there were many things that were much more powerful than it.

Even so, I can tell that the pill I just took was no ordinary poison.

You said it wasn't precious. Of course, I appreciate it.

Qing smiles with a mixture of guilt, burden, and gratitude.

What can I do but say thank you for something I've already eaten?
