\chapter{The New Semester Has Begun (13)}

Puck, a soft ringing sound.

It wasn't a loud noise, but the crowd's expressions were all distorted, as if they were about to cry.

Well, some attacks were painful just to watch.

Surprisingly, the sight of blood splattering from a fancy swordsmanship or a fancy martial art was felt less painful than a properly dug fist.

That was because it was a pain that everyone had experienced at least once in their lives.

Especially in the harsh Zhongyuan, where if you don't throw a punch after an argument, you're considered a coward.

"Ugh."

Cai Shengxia rolled on the floor.

It was because the true master's punch, which contained the secret of nuclear fission, hit the vital point.

What on earth was the secret of nuclear fission!

What kind of noble technique must it be to make someone who was running wild without thinking just fell to the ground so meekly?

Nuclear fission was a great enlightenment that embodies the true meaning of a living sword, or rather, a living strike.

It uses internal energy but does not emit it, so it was used to control the master's body, and does not harm people with true energy.

It was also a meticulous consideration to understand the opponent's capabilities and not only save their life, but also to prevent future damage from injury to their bones.

However, it was a great idea that values human life and preaches love for humanity and humanity to the entire world, as it completely neutralizes the opponent.

If you could just summarize this in one line?

Hit as hard as you can without making them a cripple!

Of course, this was because Qing's studies were lacking.

A true master who has mastered the secrets of nuclear fission uses his internal energy rather than his strength to strike the insides with the techniques of the internal double-strike method, without causing harm to anyone.

Thus, the true secret of nuclear fission was to reach a point of invincibility, where even the most potent and powerful blasts can penetrate.

Anyone struck by this nuclear retaliation will experience excruciating pain, as if their limbs were being twisted and split in half, and regardless of whether they were adults or children, men or women, they would roll around on the dirt floor, crying, snot running down their face, and even drooling.

However, since Qing was still only at the beginning of the Ximen Surin-style Nuclear Fission-type Permanent Peace Divine Art \~Pain Knows The Answer\~, she was limited to using techniques that relied on external power.

The result was Cai Shengxia's appearance with big tears hanging from his eyes, but not flowing down his face.

Qing looked down at the sight and thought.

\textit{Seeing him trying to hold back the sound of his choked breath, it seems he still has enough consciousness to save face.}

\textit{Hmm, more practice was needed.}

\textit{If it had been Master's original nuclear fist, he would have been rolling on the floor crying and losing face.}

\textit{Is this the difference between Unrestrained and Profound Realm, the difference in class?}

It was a moment of renewed awareness of the greatness of the Master.

Anyway.

Despite the pain, Cai Shengxia was struggling to get up.

Cai Shengxia stumbled as he tries to get up, falls to the ground in a heel, and then barely managed to get up again, using his sword as a cane.

Because the breathing was still tight, a faint murmur, almost like clothes flowing down, was caught by Qing's superhuman hearing.

"Ugh, that, blood…"

Blood?

"Avoiding was fatal……"

Qing nodded to him.

\textit{Hmm. Are you out of your mind?}

That was when.

"Oh, my friend! That's enough. I apologize, Instructor. My friend seems a bit overly ambitious. May I apologize on his behalf?"

A man who climbed up without permission bowed his head while supporting Cai Shengxia.

In fact, it was more like suppression than support.

The arm wrapped around the shoulder were tightly covering Cai Shengxia's mouth, so Cai Shengxia, who still had difficulty controlling his body, can only glared.

The look in his eyes seemed to say, 'Who the hell is this guy?'

Qing looked at the young man who has barged in.

"What about you, Young Expert?"

"Haha, I am Zhang San from Foshan. You are the instructor, so please be informal."

"Zhang San?"

"Yes, it's Zhang San a simple ronin. Everyone asks if it's an alias, but I can't blame my parents for that, can I? I suppose it's the fate of the third son of the Zhang family."

A wide, narrow eye with a bright smile, and a gentle, sly attitude that was beyond compare.

There was no one more suspicious than him, as he even used an alias that sounded like a fake name to anyone who heard about him.

These types of people, when they open their eyes with a serious expression, have a dirty impression, and act as a kind of dark villain.

But Qing didn't find him suspicious.

\textit{Wow, look at this guy? Seventeen points of good deeds.}

\textit{It's quite high, isn't it?}

What Qing realized while wandering Jianghu was that while there was no limit to evil deeds at a young age, there was a clear limit to good deeds.

Even children could become vicious and destroyed other people's lives.

But in a relatively young life, it wwould be difficult to accumulate Good Karma, which was the benchmark for this karmic figure.

"Isn't this the spirit of youth? After entering the academy, you'd be able to ask the instructor for guidance as much as you want, but we have an exam schedule, and the other applicants are waiting. Do you really need to bother the instructor for so long? I have to give this guy a good talk-"

"Muhup, what, you, who, ugh."

"-A really good talk."

In fact, it was already a difficult situation.

\textit{I was curious about how ugly he could become, but I also felt a bit awkward about facing him head on.}

\textit{Well, the other guy seems like a decent person.}

\textit{I'll have to write him a special recommendation for the next exam.}

In this way, Zhang San drags Chae Seong Ha away and retreats.

It's a very familiar sight to see him covering his mouth, tying his arms, and pressing down on his stomach to subdue her, pretending to support him naturally, but whatever.

He might have practiced the Golden Hand style.

As Qing walked back to the examiners seats on the second floor of the temporary building, her eyes were suddenly dazzled.

It was because the famous super-white teeth of White Tusk Sword Wu Zhangyue reflected the sunlight.

When their eyes met, Wu Zhangyue nodded.

Because his gaze seemed burdensome, Qing nodded slightly in response and quickly returned to her seat.

Then Sima Chunfeng opened his mouth again.

"Indeed, he's a talent worth keeping an eye on. And that Zhang San is quite suspicious, but it's clear he's shown good intentions, isn't he?"

"Is that so?"

"The Heavenly Blossom Sword's initial, unexpected strike—yes, a surprise attack—subdued him, thus saving the faces of both Young Expert Chai and Great Expert Wu. Chae Ga possessed formidable martial arts, but his weaknesses were clear. Great Expert Wu wanted to test him, so he yielded, and his defeat wasn't really a defeat."

"I didn't think about it that much."

"No, then, in the second spar, there would have been no reason for Heavenly Blossom Sword to avoid Young Expert Chai's sword and then subdue him with your fists. Because if you pulled out your flute and confronted him, it would be like saying Heavenly Blossom Sword blocked an attack that Great Expert Wu couldn't block. It's a bit of a stretch-"

Sima Chunfeng rose an inch from her sitting position.

Her side was her weak point.

In fact, it was everyone's weakness.

"Ah, Heavenly Blossom Sword? What, what-"

"Zhuangzi said, ‘A wise man iss silent.' So, isn't the best way to become wise to remain silent forever, for the dead are the wisest?"

"What nonsense is that? Ah, hehe, Heavenly Blossom Sword? You're embarrassed, don't you? But Heavenly Blossom Sword? The mindset of a Heavenly Mandate Knower, who will lead the era like us, is something that these lowly mortals won't understand unless you speak out loud. Let's spread this anecdote widely. Hehe, the same method twice—"

Qing's fingers were aimed at Chunfeng's side again, but she avoided them and raised her chin.

However, Qing learned the secret and gentlest art of the Golden hand, the Divine Thief's Flexing Flex.

The stray finger strangely climbed up like a boneless creature, then dug into the space between Sima Chunfeng's tightly-fitting forearm and side, squeaking, squeaking.

"Kkihyaak! Kkeukhakhak, don't, do it, kkihakhak!"

As Sima Chunfeng barely managed to cover her's mouth to stop the the choking screams, Qing thought.

\textit{Anyway, the superficial smart people are making a fuss because they want to boast about what they knew.}

\textit{In this respect, I realized how great Xue Ga-nom is, who was the pinnacle of brainpower but always remained humble and did not show off his knowledge.}

\textit{Perhaps we need to broaden the title of our intellect to include other provinces as well.}

\textit{Three Province's Best Intellect?}

Meanwhile, Sima Chunfeng, who had burst out laughing for while, collapsed on the table, gasping for breath.

No, I thought you were going to take a break?

"Ugh, hoo, hoo, and, hoo, since  Young Expert Zhang understood the meaning of Heavenly Flower Sword's intention and intervened at the right time, hoo, hoo, if she face him a third time, the Heavenly Flower Sword's intention for the Great Expert Wu would be in vain."

Sima Chunfeng was a stubborn woman who ignored even the lack of oxygen and difficulty breathing and kept talking.

"Whew, huff. If you end up colliding head-on, Great Expert Wu's reputation will fall to the ground and Young Expert Chai would end up rolling around- huff, uh, ah, that, that won't do…"

Finally, Sima Chunfeng's eyes trembled as she was grabbed by the side again.

Qing answered.

"Okay."

Keuhahhihahaha A laugh that should never come out of a woman's mouth burst out.

Of course, she gave up on the side she was caught in and covered her mouth with both hands so it couldn't be heard down there.

Somehow, the examiners who had come up together, especially the members of the Wulin Alliance Military Division, were smiling mischievously as if to say, 'She's met the real deal.'

It's a warm teasing that says, 'This bitch finally has a friend, not an accomplice to bullying.'

"Hoo, hoo, Heavenly Blossom Sword, hoo, if you think you've won with this, you're very mistaken, hoo, hoo."

Qing suddenly realized.

\textit{Chunfeng, this guy has a subtle reaction, no, her reaction is really amazing.}

\textit{If I teased Lan-ah a little, she would immediately start shedding tears (fake tears) with a look of betrayal on her face.}

\textit{Gunyeong would simply say 'Don't', forming a subtle wrinkle between her eyebrows, as if she were there but not there.}

\textit{San was annoying because he pretended not to be upset but secretly gets upset.}

\textit{I feel a bit sorry for teasing Young Lady Gongsun or Young Lady Murong.}

The only thing that keeps him going was that he gets a little tired and occasionally gets stabbed.

Then the first exam begin again.

Actually, the role of exam was not that fun.

\textit{Since I'm in front of the public, I have to maintain that awkward posture of a Ximen Surin-style beauty, and since I've come this far, it's better to write the evaluation report sincerely rather than just blankly killing time.}

"Hehe, this applicant was from Jeongnam, Jiangxi Province. It's somewhere between Jiangxi and Guangdong, and geographically, it's a place with lush vegetation, soft soil, and abundant water. This makes them naturally strong and sturdy from a young age. Temperament was something that's passed down through generations. So, how about focusing on these aspects? Hehe, Heavenly Blossom Sword, what do you think? Do you have anything else to say?"

"Jiangshi Province? The pufferfish sashimi was delicious. The name is a bit starnge, but is it really that tasty?"

"Are you referring to Seosiyu? However, Seosiyu is a dangerous dish that even now kills a thousand people a year due to improper preparation. For us pioneers, charged with leading the times, the most important thing was is own health, and second only to that, the preservation of this precious being, don't you understand?"

"Shh. Let's get started. We'll talk about food later. I understand Sima-lang's passion for food, but you have to be careful about the time and place."

"……? This, this, this, this petty trick."

\textit{I guess I'm lucky that Sima Chunfeng, who sits next to me and talks nonstop, was there.}

\textit{Looking at it this way, we can see that Cai Shengxia is a talent beyond the standards.}

\textit{It's because the kid was immature, and I don't think he has any malicious intentions, so if he doesn't withdraw, he'll probably make it to the final round without a hitch.}

In fact, there was no reason for a talented person with such great dancing skills to enter the academy.

Most of the applicants were between third-rate and second-rate.

Qing tried hard to find a good point, even if it was forced.

"Hmm?"

One candidate enters the testing ground.

"Who's that guy?"

"Heavenly Blossom Sword? Do you see something? Let's see, Duan Diao from Geli County, Guizhou Province. He's a nobody."

Qing saw people a little differently.

With numbers sticking out above their head, even if she tried to look at them normally, she couldn't help but look at it with colored glasses.

Somehow, a guy with a deep red Evil Karma came out and said he would enter Yizheng Martial Study Hall?