\chapter{The New Semester Has Begun (8)}

"This concludes the morning exam!"

The exam proctors announces the end of the morning exam.

People dispersed with regret.

Some of them noticed that the hour and a half meal time from the beginning of the morning to the end of the evening was not that long when so many people gathered at once, so they quickly ran away.

Of course, those who sat in the front row continued to sit still, showing their unwavering determination to wait for an hour and a half like this.

A street vendor, raising his voice as if he had been waiting, is smiling happily as he sells food at a rather expensive price.

Meanwhile, Yang Qi, the seventh son of the Yang family, was out of his mind.

\textit{Me, First Class?}

The sense of the world he glimpsed from the Sword Qi, the boundless sense of liberation he had never felt before, seems to be stuck in his heart and lingered.

Innate Qi is a part of the body that has come out, and the inside of that unmanned person, a new limb has sprouted and was sweeping the world, so what would that feel like?

Something that is difficult to describe in words, like a blind person opening his eyes.

"Excuse me."

If someone hadn't tapped him on the shoulder and spoken to him, Yang Qi would have continued to blankly reminisced about that moment forever.

When Yang Qi came to, a middle-aged man with a long scar running from his cheek to his lips was looking at him.

If it weren't for that, he was a middle-aged man who would have made a woman cry.

"Uh, um? Who are you?"

"My name Jogaksan. I'm embarrassed to say it, but I'm also known as Virtuous Gale of Qinghai."

"Ah! So you're Great Expert Jo."

"First of all, congratulations. How does it feel to have reached First-Class Realm?"

"I-I can't believe it. Oh, uh, did I even greet Heavenly Blossom Sword? I couldn't even say thanks in the panic—"

At that, Jogaksan laughs.

"No, you bastard. Since you had bowed deeply and cheered three times, even Heavenly Blossom Sword would have understood your feelings."

"Oh, did I? Hurrah?"

"It wasn't a cheer, but it felt that way. Now, these are my younger brothers. Our youngest is entering the Yizheng Hall this time, and I think you and him could become good friends. As a token of my gratitude, I'll treat you to a meal."

Yang Qi's expression becomes cloudy.

"Can I pass? I have no background, and I'm just an unknown person in Jianghu."

"Haha, this bastard. Who dares disqualifying a young man who become a First-Class Realm thanks to the teachings of Heavenly Blossom Sword? That's newsworthy for the publicity of  the Yizheng Martial Study Academy. Besides, what would that do to the reputation of Heavenly Blossom Sword? Hmm, you should study not only martial arts but also how Jianghu operates."

He was saying that Yang Qi would definitely passed.

The corners of Yang Qi's mouth rose.

Jogaksan think it was so cute in that way.

\textit{This guy can't even control his facial expressions, and he's new to Jianghu, so he's completely trustworthy.}

Jogaksan was worried about his youngest brother, who was already a bit clumsy and weak-willed.

\textit{If he stick with someone who is too smart, he will likely get swayed, but if he stick with someone who is as smart as him, he will end up being even more foolish because now there are two fools. So, I want him to make friends who are moderately smart, but also strong and capable.}

"By the way, how old are you?"

"Yes, I'm turning twenty-three this year."

"Really? That's perfect. Youngest, you're the same age, right?"

"Um, my name is Ma Dazhe,"

"Haiyaa. It's so annoying how people of the same age treat each other with such politeness. Isn't that right, Young Expert Yang?"

"Come on, let's stop this and have a quick drink. I'm a wanderer, so my pockets aren't exactly deep, but on this fine day, I'm sure I can still quench your thirst."

If Yang Qi was uncomfortable, it would have been a foolish idea to make the youngest friend of his sworn brothers and stuck him on.

Fortunately, Yang Qi came from the countryside and didn't know anyone.

Besides, it's a welcome thing to hear that they have plausible nicknames and are also famous swordsmen.

Since there were seven of them, they had to do some legwork to find a suitable restaurant.

After an event like this, where everyone was busy sharing what they had seen and felt, the restaurant was bound to be busy.

This appreciation is a matter of discernment and knowledge.

'This is how much I see, and this is how much I know about martial arts'. It's also a form of self-praise.

Some people sell these stories for money, so they are called 'seller'.

"Everyone, have you seen the exam? Hmm, I'm not sure if you're all familiar with the realm of martial arts, but a martial artist who can freely use their limbs and handle betting is called a second-rate martial artist. And among them, the most outstanding second-rate martial artists fill their swords with energy, increasing their strength. Not only do they not break, but they also maintain the sharpness of the blade. It's a martial art called "Eogi Chunggeom" (a sword filled with energy). It's the art of filling a sword with energy!"

Ahem, the salesperson clears his throat.

"But, after Yang Qi Sohyeop's final strike, did you see the mysterious, shimmering blue aura glinting across his blade? This is the manifestation of the art known as sword energy. The sword energy that filled his weapon finally revealed its colors. This means Yang Qi Sohyeop has reached first-class status! His repeated deep bows and thunderous expressions of gratitude are proof of this. But what kind of enlightenment could suddenly allow a martial artist to break through this realm? That is..."

The storyteller was taking a deep breath and suddenly-

"Ahem, I'm a little thirsty."

"Oh my, it's already starting. Server, bring that guy a bottle of something really refreshing!"

Jogaksan giggled and filled Yang Qi's glass.

"It's all about you? Congratulations on making such a splash in your first appearance in Jianghu."

Yang Qi's face turns bright red.

He felt very shy and awkward when his name came out of someone else's mouth, from the mouth of a man who always talked about distant heroes.

Since the server was also in the audience, he quickly placed a bottle of alcohol in front of the storyteller.

But the storyteller leisurely filled his glass and drank it, knowing the importance of taking his time.

"Wow, that's refreshing. Hehe, thank you. Now, what are we talking about? So, how did Young Expert Yang manage to reach first-class status in that very place? Now, everyone, do you know the saying, "Chu-gung-gwa-hyeol"?"

There's a lot of gossip about him.

Some people agree, saying, "Yes."

Some people ask, "What is that? Why are you talking about something you only know?" "What kind of dish is that?" "Is that damned thing already asking for food?"

"Chugung and Hyeol is a treatment method originally found in medical books. It's a technique that strikes the blood vessels to open blocked blood vessels and benefit the meridians! However, a master with peak qigong can also apply it to induce an opponent's true energy! Heavenly Blossom Sword imparted great teachings through this, and Yang Qi Sohyeop immediately attained enlightenment!"

He didn't actually make up words that didn't existed.

Chugung and bloodletting is actually one of the most widely used medical techniques, and its effectiveness is guaranteed by all existing medical books.

However, that does not mean that it is a trustworthy word, because Chugung and Hyeol is a technique called massage in the Western language, which involves kneading rather than striking to loosen up knots and melt away fatigue and turbid energy.

If it had seemed like enlightenment could be achieved by beating up the blood vessels in the first place, the martial arts world would have ended up in a much more horrific state.

Because all the teachers in the world would have been obsessed with beating up their students.

Of course, there are still quite a few teachers who beat up students hard, but anyway.

In addition, there is also talk that the Cheonhwa Sword, known as the ultimate sword, induced true energy through the use of the Chugung and Blood.

Usually, when you say something like this, someone will come out and refute you.

But that person is Heavenly Blossom Sword, and he will be staying in this city right away and taking his place as an examiner in the afternoon.

It is not easy to come out and say, "There is no way that would happen," so to speak.

"Oh!" "That's the situation……!"

"Do you know what's even more surprising? The fact that Heavenly Blossom Sword immediately recognized the essence of a mere ronin's swordsmanship, even if it was just by observing his nameless skills!"

The story teller spoke without even knowing that the mere ronin with nameless skill was right there.

The number one cause of death of the storytellers was a mistake in the way they moved their lips and got stabbed in the neck.

But, to Yang Qi, who was listening, it didn't seem like a wrong thing to say, and even if it weren't for him, there wouldn't be anyone in this city who would draw their sword so carelessly.

"The invincibility of the Cheonhwa Sword has been well known since she was twenty, at the peak of her power. However, today, I have glimpsed a glimpse of true genius. I dare say, she is a true genius among geniuses, capable of seeing through the truth at a glance."

So, naturally, the atmosphere was like, 'Now, let's start praising Heavenly Blossom Sword.'

"Well, was it really a case of bloodshed?"

The third or the fourth brother quietly asked.

But Yang didn't know how to answer it.

Because he've never experienced it before.

"I don't know for sure. But it was a truly mystical experience. The Heavenly Sword pushed and pushed, but my limbs felt familiar as if they were in their proper places."

Because that's where the limbs should be originally.

"True Qi also moved around my body freely, as if it was asking why I didn't do this before……"

Of course, it was clear that Jin-gi had to share his strength with his bones to keep himself from collapsing, and his mind, which had reached a state of extreme concentration, unconsciously guided Jin-gi.

But just a moment ago, a second-rate, nameless military officer from the countryside, what kind of profound theory of martial arts could a country bumpkin have learned?

So, what if I ask you?

"Huh. So it's really a method of questioning and bloodshed?"

"Big Brother, could it be that the Heavenly Sword has actually reached a higher level?"

"Isn't she twenty-two this year? At that age, it's nothing short of miraculous to be at the Transcnednet Realm. Rather, it's more accurate to say that her own insight has reached its peak. Isn't she the successor of the Tathagata's Divine Palm? Is the Tathagata's Divine Palm some ordinary Divine Art? Isn't it the most rigorous of all the Qigong practices, the most profound and foremost Divine Art in the world?"

If Qing heard of it, she'd say 'You're talking about me? Of course, I'm already great, but it's a bit too much.'

But there was no Qing in this place.

"Ah, if only I could learn just one branch of the Divine Art, just one Movement, I would have no more wishes in my three lives."

"What you're talking about when you can't even master the Cheoncheolgeom? Do you think Divine Arts are Divine Arts for nothing? The depth itself is different, so even if you learn it somehow, how can you use it? That's another story. Do you think a dog can run like a horse if you put a horseshoe on its paw?"

"Big Brother. You're being too harsh."

"But isn't the sole of Fourth Brother foot bigger than mine? I was weaker than you when I was your age. So, in that sense, aren't you already a better younger brother than your older brother?"

"Ahem, that is-"

In Yang Qi's eyes, they are truly good sworn brothers.

Perhaps I too could gather like-minded friends, form a bond of brotherhood, travel the world, and make a name for myself by striking a deal.

When I think about it, it's a feeling of grandeur in my chest.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was the middle of the first exam, and the city was overflowing with test takers, making it difficult for the examiners to move around freely. Naturally, they had no choice but to eat lunch at the temporary testing center in the temporary academic building headquarters.

If you ask Qing to name the three most enjoyable things in the world, it would be breakfast, lunch, and dinner.

If we were to rank them in order, it would be dinner-lunch-breakfast, but you could say that it's simply a ranking of the dishes served in large quantities.

It's a real win-win, because you get to enjoy the most enjoyable thing in the world three times a day.

It's better if you go there with someone you know.

"Oh no? This can't be happening! What is this energy!? Something indescribably cute...!"

"Gege!" "Xiang'er!"

Inside, Zhuge Xiang, who hadn't grown at all in the meantime, was playing with her short legs.

Then, I suddenly stopped and stopped.

It is Zhuge Xiang who must rush in.

But because there is already a passenger who has taken possession of the Qing.

"Gege Sister? Who, who is that woman?"

\textit{Do children also treat each other as women?}

"Huh? This is my daughter, Ciyu. Ximen Ciyu."

"Huh? Well, then, what about the Family Head?"

A fluent vocabulary that is not lacking.

It was a side of her that befitted the younger sister of Zhuge.

\textit{What can I say, since Zhuge Xiang was already reading military books by reading a lot of books?}

"Family Head? It's me. I'm Chiyu's father."

At that, Zhuge Xiang sighed in relief.

"Hmm. Changbin?"

"Huh? No, huh?"

"Okay. Changbin, you should get to know your niece too. I need to share the joy of reuniting with Xiang'er."

Qing gives Chiyu to Chang-bin.

It was also a punishment for pretending not to see the generous chairman who was being lenient even though he was a ghost member and avoiding him.

"My niece… Oh my, Little Niece, hello? My name is Changbin."

However, surprisingly, he was be able to received the child skillfully and greeted her politely.

\textit{What? So a child doesn't seem to fall into the category of a woman? }

Of course, that's to be expected. If he was to stutter because he thought Ciyu is a woman, it would be way more problematic.

It was quite a refreshing sight for Qing.

Originally, in front of men, Changbin was the world's most cheerful man and the romantic prince who stole the hearts of women from all over Zhongyuan, but now, Qing was able to see a side of him that had never been observed before.

\textit{What? You talked? No, you're good at talking?}

\textit{Changbin can talk? This is unbelievable.}

But it wasn't a situation that would last long.

Because Seol-i-ri, who had her position taken away, was emitting a cold chill.