\chapter{The New Semester Has Begun (11)}

Sima Chunfeng's whispers were heard from the side.

"Indeed, he possesses a spirit of victory. It's a virtue that no warrior can lack. Hehe. Is that person truly qualified to share the loneliness of those who stand alone and lead?"

"What's with the pride? If you can't tell the difference and just barge in whenever, was that pride? It's just ssamdak. Hmm, ssamdak, I want to eat it wrapped in radish kimchi and grilled over an open fire."

"……? Heavenly Blossom Sword?"

Qing was not a very competitive person.

If you get hit once, your eyes will roll back, but it's not like humans were creatures who naturally get angry when they're hurt, so it's not like they deviate from that universal tendency.

\textit{But, should I say, a challenge?}

\textit{After hearing it, one thing was certain.}

\textit{If I win, I'd only break even, but if I lose, I lose.}

\textit{Come to think of it, there were quite a few elders who said, 'Since we've met here, let's have a look at the sword.'}

\textit{I could clearly see how much of a favor they'd have shown me.}

\textit{From the elders' perspective, it's actually as easy as twisting a child's wrist, and if they get hit even once at a time when it's not even a proper exercise, isn't it a huge loss of face?}

Actually, there was a time when she almost broke her friend's father's head.

So, it's a matter of etiquette.

Qing was not a hard-line Confucian legalist.

But if you want to ask for favors, shouldn't you first be polite?

From Cai Shenxia's perspective, there was nothing to lose even if he lose.

Even without winning, just a few cool fights would be enough to make people excited and call him Young Azure Dragon and whatnot, making his name known.

However, Qing was not a person who moved based on these profit and loss calculations.

Rather, because she places too much value on recognition, she was close to being the one who suffers losses by jumping in without being able to distinguish between what she should and should not participate in. She was the embodiment of a busybody, who ends up meddling because she cannot bear to see someone she knows was in trouble.

Rather, that's why she got angry.

As much as she valued recognition, she also placed a high penalty on ingratitude, and thus the crime of contempt was added.

I mean, that's annoying.

In fact, Qing's favor was quite cheap.

If you don't try to stop people from coming and become friendly with them, they will just greet you like old friends after one drink.

If you just pour her a drink and ask her to spar with you once, she'd say yes without even pretending to think about it. Isn't she a kind person?

But this was so annoying.

"Oh, is this the spirit of the current generation!" "Accept it!" "Heavenly Blossom Sword!" "Heavenly Blossom Sword!" "Young Azure Dragon!" "Young Azure Dragon!"

It's not easy to pull out now that people have already started cheering and chanting that nickname.

If Qing had just been a spectator, it would have been different, but she was sitting here as an instructor at the Yizheng Martial Study Hall, an outer disciple of the Divine Maiden Sect, and a disciple of Ximen Surin, Heavenly Blossom Sword.

If she refused, they'll say that Heavenly Blossom Sword was withdrawing because she lacked confidence.

If such rumors were something that Qing had to endure entirely alone, she wouldn't really care what anyone said.

If it affects the Wulin Alliance, the Divine Maiden Sect, the Master, and those involved, then of course she will be concerned.

Suddenly, a thought flashed through Qing's mind.

\textit{Ah. So this is how things are in Jianghu.}

\textit{Because I am not one thing.}

\textit{Wherever the enemy is, the image of a teacher, disciple, and close friend tightly intertwined and held on.}

Suddenly, the grumpy face of the old Emperor MuQing Mucheon flashed through Qing's mind.

Dokgo Gugeom, I will save the end of the sword.

Alone and alone.

The salvation of the sword was not important.

Yes. Who among those who wield a sword wouldn't want to see its end?

Everyone wants to touch the sword.

The path of the Great Emperor Mucheon was one of solitude.

He wanted to transcend all things in this world, break free from this tangled web of fate, and dedicate his life solely to his own sword.

That was why Emperor Mucheon ran rampage.

He cleared out the Demonic Cult, swept away the Blood Sect, and caused a great uproar in the Imperial Palace, clearing out  Zhongyuan.

To sort out the remaining ties in this world, to shake off even the last shred of regret.

The old man, who was so concerned about his appearance that he didn't fit in with his juniors, cleared up the remaining troubles.

And then he left and disappeared without a trace. Was his last year a time of ascension, or was he a wanderer and died alone on the forest?

But one thing was certain.

He must have held the sword tightly until the moment he took his last breath in this world.

\textit{Of course it's respectable, but I'm a bit…}

\textit{Even if I succeed, what good will it do if I'm the only one in the world?}

\textit{There, I can tease even the most humble of people, show off to the elders, receive their love, and make people say, "Awesome Heavenly Blossom Sword!" and beat my forehead until it breaks. That's the only way to become a master.}

\textit{Above all, if I have a sword, I must protect our weak kids.}

\textit{You can't do sword fighting alone, or rather, sword fighting requires an opponent, so what's the point of just swinging a completed sword in the air?}

'Tsk'

\textit{Oing? I think I heard a displeased click of the tongue from somewhere.}

"Heavenly Blossom Sword?"

"Ah. I was just thinking about something else."

"Indeed, even in times like these, such composure! As expected, she's on par with Sima-lang. Heh, but, isn't this the time to take it easy?"

"Hmm."

The image of the great emperor Mucheonmu Qingdae keeps coming to mind.

Perhaps he eventually achieved something on his own, but after completing it, he wanted to let the world know that he had done it and that he was right, and that he wanted to let it be known to his disciples or descendants.

If you keep pushing like this, it will be difficult.

You can lead a horse to the river, but it was the beast's will to drink water. No matter how good the opportunity is, it was better to go alone.

Qing looked down at the crowd, who were still chanting her name and shouting for her to fight.

And Cai Shenxia who looked somehow proud.

Suddenly, Qing's annoyance gradually subsides.

\textit{Even the image of the Great Emperor Mucheon was like that of a master who wants to pass on his grandfather's legacy as a perfected martial arts master.}

\textit{I don't know if Grandpa MuQing Mucheon Daeje was trying to do something for me and keeps telling me to take a bite of Dokgohaeng and say, "This was really delicious."}

\textit{How can you jump to conclusions just by looking at a stranger, let alone someone like that old man whom you've met so many times that you've grown attached to him?}

\textit{Maybe he doesn't have any dark intentions like making a name for himself.}

\textit{What if it's the first time he's been to Jianghu?}

\textit{He may not realize that this is rude.}

\textit{He might want to solve it right away because he doesn't know how strong he really is and he's curious about the level of Wulin.}

\textit{No, it could be a competitive spirit that makes him want to meet a strong person and fight them, like Chunfeng said.}

As Qing get up from her seat, the cheers of "Ohh …

The testing center had a somewhat festive atmosphere.

Qing thought as she stood on the examination stage.

\textit{Well, I'm going to win anyway.}

Qing was surprisingly a master of Unrestrained Realm.

Compared to the highest level, it was a distant master who feels unpleasant, and among them, it was the Transcendent Flower Sword of Heavenly Flower, which was so great that it deserves to be called the master three times.

The Baek-A-Geom Daehyeop's super-peaking Geon-Chi was so amazing that even I am surprised by his super-white teeth that even the Cheonhwa Sword cannot compare to, but in terms of martial arts, I'm sorry, but he can't compare to me.

\textit{Even if I win, I'd still have my principal.}

\textit{Just because I don't get anything out of this sparring, doesn't mean my opponent shouldn't get anything out of it, right?}

\textit{So, as a senior of Jianghu, I should show some leniency.}

\textit{Just adjust the amount appropriately, say a word of encouragement, and then step back, and that's it.}

"I am Ximen-Qing."

"I am Cai Shengxia. Hmm. Indeed."

Cai Shengxia looked at Qing up and down.

\textit{This kid is really rude.}

\textit{No, stay tolerant. Stay calm.}

Qing held back.

Then, Cai Shengxia smiled brightly, revealing his white teeth.

It was a smile that was inferior to that of the previous person who had been attached to Baek A-geom Oh Dae-hyeop.

"From what I have seen and heard, eight out of ten people in the world would not hesitate to call Young Lady Ximen the most beautiful woman in the world. Could you perhaps give me the opportunity to witness your beauty?"

\textit{Ah, I see.}

Qing has attained enlightenment.

\textit{I don't know who your master is, but he taught you how to dance very well, but it seems he didn't teach you etiquette.}

Not showing your face meant you didn't want to show your face.

It's such an obvious thing, but there were people who don't even understand this obviousness.

Of course, since it's easier to cover your face, you don't have to control your facial expressions, and since everyone in the restaurant was looking at your face, the series of gazes that give way to your skin instead of eating by holding the food up to your cheek, philtrum, or chin were just annoying.

\textit{But you insist on showing you what I intentionally hidden?}

\textit{Are you just curious about that?}

\textit{This is just rude.}

\textit{In this respect, I am reminded of Master's grace.}

\textit{She emphasized etiquette and formality, so weren't she trying to make a beggar who ate anything into a human being?}

\textit{And now I am also in a position to teach.}

\textit{This kid needs some etiquette lessons urgently.}

"I am here to speak, not as a woman, but as an instructor of the academy, and as an evaluator of the examinations. This was in line with the spirit of the Yizheng Martial Study Hall, which states that men and women should not be discriminated against in the path of learning. Otherwise, why do you ask to see my face? Surely, you, Young Expert Cai, don't distinguish between beauty and ugliness when pointing your sword?"

In fact, surprisingly, many people do!

Even among women, if they were beautiful, there was a tendency to try to subdue them rather than kill them, no matter how vicious the devil was.

However, it was not a question that could be answered openly, so Cai Shengxia stuttered, unable to find the words to say.

"A warrior proves his mettle through his martial arts. The test is still ongoing, so let's leave the discussion aside for now. Now, let me show you my skills."

It was a fatalistic statement that he would speak out on his own and prove it with his martial arts skills.

Even the Supreme Master of the Tang family acknowledged this as the invisible poison, the tongue of the devil of hell.

Qing widens her stride and lowers her pelvis.

Place your left hand lightly next to your chest, and extend your right hand with your palm facing upward.

This was the basic posture of a common recommended technique in martial arts.

Cai Shengxia's expression was one of disbelief.

"Aren't you going to draw your sword?"

"I haven't decided yet whether you're worthy of drawing my sword, so I'll decide after seeing Young Expert's skill."

And then Qing put her four long fingers together and made a beckoning gesture that, if you had to describe it in words, would be something like, 'Come on, fight me'.

"Okay, let's go!"

Cai Shengxia took his first step with the same gentle technique he had shown earlier.

The tips of the feet pointed obliquely towards the enemy.

As the center of the body moved forward, the body naturally rotated, and the rotational force was added by swinging the two long arms.

Cai Shengxia's body turned once, twice-

At that moment, Qing's eyes flashed.

The sole of the foot that steps forward, a jet-black magical energy pours out from the Yongcheon point and the body flies, it was a legendary new skill of Shinto that moves the body by striking the air.

It was also considered one of the three greatest Qingqong in the world, along with Kunlun's Cloud Dragon Eightfold Path and the Wudang's Jeunjong.

Originally, it was characterized by its speed, which was the best in short distances, and its movements that were as silent as a ghost.

Normally, it's Cheonma Gunrimbo Kwang Kwang Kwang, One Two Three Three Baek, which was the maximum speed, so I didn't use it that way often.

Qing's arm bent like a whip.

It was an optical illusion caused by the trajectory of the hand's afterimage at such a fast speed.

As Cai Shengxia was about to make his second lap and begin his third, he was suddenly shocked by the sight of a palm that was just a stone's throw away.

And tsk tsk!!!

The palm of the hand containing the secrets of the nuclear fission chain, the Ximen Surin-style training method, struck the exact center of Cai Shengxia's back.

"ARGH!"

Cai Shengxia immediately screamed and twisted his left and right arm joints, pointing them at my back, and like a sparrow, he jumped on both feet and ran around the examination stage like a zombie.

This was because the two extreme pains of burning heat and freezing cold rush in from the center of the back, behind the navel.

The flexible, unmanned penetration allows the affected area to be rubbed cleanly with the back of the hand and the palm, but the right elbow that was flashed and the left elbow that was bent back as far as possible were a bit awkward.

"Owww……"

Even among the crowd, groans of pain erupted.

It was a voice of sympathy that was especially raised by married men with spicy wives.

Cai Shengxia, who had been pacing around the training ground for a long time, caressing his back, finally shouted out as if the pain was subsiding a little.

"W-what was this? A surprise attack!?"

Tears welled up in his eyes, showing how much it hurt.