\chapter{The New Semester Has Begun (9)}

As they entered the banquet hall, Qing's eyes suddenly became dazzled.

Because a giant light was installed in the center of the banquet hall, what was that? Was it oiled or something? Qing carefully examined the monk's shiny, bald head.

You really did apply oil? What the heck? Is the amount of baldness in a monk's head even a measure of handsomeness?

Of course not.

Originally, monks had to shave their heads twice a month on the 13th and 28th days, and when they shaved their heads, they would soak their hair in oil to protect their scalp.

In Zhongyuan, there was a perception that incense (scented soap) was a feminine item for some reason, so men just rub it with water and wash it off, and today was the day to shave their heads.

Of course, since the oil was not washed off with water, the entire head becomes shiny and shiny.

This truly shining figure was none other than Weifeng, a young Shaolin master who excelled in Shaolin martial arts, Baekbo Shinkwon, and Geumgang Bulgae Shinkong.

However, the first and last impressions of Weifeng were not very good.

"Monk Weifeng, how have you been?"

Monk Weifeng turns his head and was greeted by the most harmful beauty in the world.

A look that makes me lose my mind without even realizing it.

Was this the very Mara who tried to tempt Buddha in the past?

"Huh! Go! Amitabha Buddha."

Weifeng chant hurriedly.

Then, he raises one hand and shows the blade, bowing while raising the banjang, a unique greeting technique of Shaolin.

"Heavenly Blossom Sword, you have been very refined."

It was directed at Zhuge Lee Hyeon.

"Monk? You're pointing the wrong way."

"Ahem, excuse me."

Weifeng hears Qing's voice, adjusts the angle, and raises the banner again.

\textit{Now that I look at it, Weifeng has his eyes tightly closed.}

\textit{What is it? Is it some kind of training?}

\textit{Since there is silent meditation, it wouldn't be strange if there are blindfolded meditation.}

"I heard you're taking on the role of instructor for the Youth Division this time? My daughter is entering the academy this time. Come gree the instructor, Ciyu."

"Hello. I'm Ximen Ciyu."

"The child is truly, umm, truly, umm… Namu Amitabha."

Weifeng, who had slowly opened his eyes, looked at Ciyu and was speechless again.

It wasn't the eyes of a human being, but rather the gaze of a corpse. The pupils were dark and lustrous, and the depth of the eyes was so deep that it was impossible to read what was inside.

"The young lady has had a very hard time."

"Please take good care of our little one, Instructor. She's been so spoiled lately, so I don't know if she'll be able to adapt."

"Ahem, as an instructor, I will do my best to train all the disciples."

This means that he won't give her any special treatment.

It's already completely blocked up, and Qing feel relieved because it seems like he's not the type of person who would say 'yes, yes, yes' just because Ciyu's a kid.

"Of course. Please teach her sternly. Children were meant to be raised strong. But I heard you train them based on the Yijin Cleansing Method? Could you elaborate?"

"That's the same training as the novice monks at the headquarters. Please understand that I can't speak carelessly about matters pertaining to the headquarters."

"Hey, are Shaolin and I strangers? Please don't do that between us. Okay?"

"Amitabha Buddha, Avalokitesvara Bodhisattva."

\textit{Anyway, Weifeng seemed very uncomfortable, so maybe it was because he met the parent?}

And then, it was mealtime, the only pleasure in life.

Changbin was a man of consistent words and actions.

In keeping with Changbin's usual saying that alcohol tastes better when a woman pours it, when a woman pours it, it tastes so good that Changbin looked down at his glass and gets endlessly drunk on the alcohol.

But this time he couldn't see any alcohol.

No matter how small a child is, if you put them on your lap, your view will be obstructed.

Changbin, who needed an excuse to get away from the dizzying world, took care of Ciyu's meals.

"Stir-fried Bok Choy."

"Oh, Little Niece, you know how to eat properly. A true gourmet always starts with vegetables. Your culinary skills are quite profound."

"Hehehe."

\textit{They were being so familiar, it makes me wonder if he's not the Third-Generation disciple of the Hwasan Sect, but rather a teacher at the Hwasan Orphanage.}

\textit{Rather, I am a little concerned about the saying that true gourmet eat vegetables.}

Of course, it's not entirely wrong, as true gourmets in Qing's homeland tend to first look for onions when eating bulgogi or stir-fried pork.

But this was a question of scarcity: which was more precious, since there was more meat and less vegetables on a plate?

Why would you approach a plate of veggies first when there was a plate of meat?

Regardless of whether one knows the taste or not, it can be said to be a challenge to the essential human qualifications.

"Changbin? Ciyu is still have a lot of growing to do. Do you think she'll grow well if you just fed her vegetables?"

"Oh, yes, that's right. I will do that."

Last time, I thought we were finally becoming a little more comfortable as friends, but if you don't see each other for a long time, it resets again and the distribution seems to be skewed towards the elderly.

"Oh, Sodojang, there's a projector here. Do you know what a projector is? It means the four treasures. It refers to four kinds of birds: duck, chicken, pigeon, and quail."

"Fish-scented eggplant."

"Look. It looks like a duck, but if you cut open its belly like this, oh my! It looks like a chicken—"

"Fish-scented eggplant."

"Small, winged creatures air said to be the most beautiful. Here, try it—"

"Fish-scented eggplant."

She was a very resolute girl.

Children have a tendency to become extremely arrogant when they see someone they think was easy.

Of course, because they were young and have young eyes, they can't tell the difference between being easy and looking easy, so problems can arise.

Anyway, it seemed like Changbin was quite easy for Ciyu.

This was something that could be considered a bit of a tantrum, but honestly, it's nice to see the kid being kid-like, so let's just leave it alone.

Especially since she doesn't have much of a childlike appearance, this was about it.

but.

It wasn't that it wasn't, but it was Qing who was worried because Ciyu preferred grass and refused meat.

Of course, I like to eat everything, so I eat meat without any problems even if there was no grass, but I think that if my priorities were wrong, it was very wrong.

However, I really hate the mushy texture, so I end up spitting out large pieces of meat, cartilage, etc.

Changbin looked at Qing's expression and-

"That, um. Eggplant with fish sauce, it's really tasty…"

"No, I told you to feed her some meat."

"She, she's trying her best, she's trying her best, ahem, so thirsty, alcohol, alcohol…"

Changbin was staring at me, and suddenly the mysterious glass of alcohol disappeared, leaving me with only my eyes rolling.

Then, surprisingly, the autonomous drinking glass moved in front of Xue-i-ri, and she was surprised by the strange technology that transcended the times.

"Uh, uh, there, um……. um."

Changbin mutters something, then nods resolutely with a determined expression.

And then-

"Little Niece? If you open the quail's stomach here, oh my, why are there bamboo shoots and shiitake mushrooms in a place like this?"

"Oh……!"

Ciyu's eyes lit up at the bamboo shoots and shiitake mushrooms.

It seems like Changbin had given up on the alcohol.

Talking to Gunyeong vs. not drinking, Changbin's choice seemed to be the latter's victory.

"By the way, Sword Friend is quite talented, are you? I didn't know you had such a talent for teaching. I was truly impressed by the way you mastered the power of the sword!"

"Sometimes, I'm afraid, too. Just how far does my power stretch? Already renowned for my architecture and medicine, and even breaking unprecedented records in my academic achievements, now even teaching? Can you call me the Almighty? Because I'm omnipotent…"

"Enough with the nonsense."

Nan-Gong Shinjae cut it off in one breath.

\textit{Hmm. Is even Sword Friend becoming harsher?}

\textit{Somehow, the closer we become, the more rude we become to each other. The closer we become, the less we know how to cherish each other.}

"So, what did you do? If you've already sparred with him countless times and knew him well, you could probably give him enlightenment, but isn't this your first time meeting him?"

At that moment, the noise in the banquet hall suddenly died down.

Everyone pretended not to eavesdrop, but they were curious.

"But I didn't do anything? He just happened to use some swordsmanship I knew, and since his posture was a bit awkward, I just gave it a little correction. It was just a coincidence that the timing was right, thanks to all the hard work he'd put into training. What ability do I have that makes him a First-Class martial artist?"

It was just as Qing said.

If you can become a First-Class martial artist just by correcting your posture, then who in the world was not a First-Class person?

So if yo just swing the sword in the right posture, you'll become First-Class?

"Hmm. That's true. But was it easy to maintain posture during a sparring match?"

"I learned this way too? In fact, I was taught much more harshly. I just pushed him to at least get him into a good position, but Master, if she felt something wasn't right with my stances, she'd hit me until I got it right. It felt like if you didn't know, you'd get hit, so you'd keep getting hit until you figured it out. So, you'd kept thinking to correct your stance. Now that I think about it, was I too kind? Should I have let him think for himself and figure it out?"

Ximen Surin's sparring was like this.

The only difference was that Qing kindly pushed and pulled Yang Qi to keep him in proper positions.

But Ximen Surin kept hitting the wrong spot, but didn't tell Qing where it was wrong.

During the transition period between the A-Qing and Ximen Qing, Qing's swordsmanship was more superficial than expected. She had a habit of making flashy movement, thinking it was looked more impressive that way.

Water, fire, and the whirlpool always know the answer.

Just as putting a person in water or fire brings out the truth, a whip with the secret of nuclear power corrects bad habits and brings out the right attitude.

"Hmm." "Indeed." "If you look at the Heavenly Blossom Sword…"

Those who pretended not to hear or were openly eavesdropping all nodded and expressed their admiration.

'Indeed, such a secret!'

'It may seem like an overly strict and violent educational method, but just looking at the achievements of the Cheonhwa Sword, doesn't it prove that its effectiveness was outstanding?'

'Ximen Surinryu's educational philosophy that produced Heavenly Blossom Sword!'

'The disciple must be beaten up.'

'So that they can think about why they were being beaten and come up with their own answer.'

'Silently and steadily, without saying a word.'

It was a moment of adversity and suffering for the applicants of the Yizheng Martial Study Academy nearby, and for the disciples of the Orthodox Wulin far away.

Ximen Qing has poisoned Zhongyuan again!

Of course, she didn't know.

\textit{Isn't it natural for teachers to beat up their students? Whether it's in movies or video games, wherever you look, the student always gets beaten first.}

For some reason, this was the perception in Qing's homeland.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The first entrance exam for the Department of Political Science and Technology was scheduled to resume at 2 o'clock in the afternoon.

Thanks to the enthusiastic audience who stayed in their seats under the hot spring sun and maintained a circular space, we were able to skip the morning process of securing space and pushing people out and get straight to the test.

Nan-Gong Shinjae stands up and waits for the next applicant.

However, somehow, it was the beginning of another battle of wits.

Well, the Heavenly Blossom Sword might come out again.

Since I'm going to take the entrance exam anyway, I want to spar with the Cheonhwa Sword, which gives me enlightenment and even fate itself.

If you do attain enlightenment, you will be in a situation where you cannot leave the martial arts world, or rather, Zhongyuan, even if you want to, and you will have to enter the realm even if you don't want to.

If you fight with the Cheonhwa Sword, you will be given the opportunity for enlightenment and even complete confirmation of admission. So, was there any reason to take the test with another examiner?

But somehow, someone has to step up.

Anyone can spot such shallow tricks right away, and if they were to even mention it, the reputation of the entire incoming class would fall.

Besides, it would be funny to see everyone rushing to fight in front of the Cheonhwa Sword while hesitating like this, and it would be embarrassing for the other examiners.

So, it was a fierce battle of wits.

It starts right here.

I understand the level of the new recruits. I don't even know that they have any intention of coming forward, saying they're bored to death.

In Qing hometown expression, it's like drinking kimchi soup at the very stage of pickling cabbage water\footnote{counting chickens before they hatch}.