\chapter{The New Semester Has Begun (4)}

After Qing left, Yoo Seon-yeop sits quietly and thinks to himself.

I heard that the Godmother said, 'Haa, my disciple achieved enlightenment overnight after reciting the nine verses of the Zhu Xiang's Heart Cleanse Mirror. As a teacher, I am upset because I am not of much help.'

Although he said it seriously, if you break it down, it means, 'My disciple was this good!' So Yoo Seon-yeop just thought, 'He must be bragging about his disciple too.'

I didn't know that one night was literally one night, without any additions or subtractions, so I guess she's just very talented.

Monk Wunue also praised it highly.

To the point where he would say that the next Greatest Under Heaven would not come from Shaolin.

But I didn't attach much significance to it either, because the word itself was filled with pride that she's having a tie with Shaolin.

Although it was said that he achieved enlightenment at a young age, it was a very surprising and mysterious thing, but reaching the state of wisdom was another story.

Even the Dagger Sword Sect has been in Hwagyeong for over thirty years, and among the seniors above them, except for the top ten best masters in the world, they were either Hwagyeong or have already passed away from old age or other reasons.

People tend not to believe things that were out of the ordinary unless they see them with their own eyes and experience them firsthand.

But Yooseon Yeop has now witnessed it!

This was true genius!

How can one know that the ignorance was not complete just by skimming through the secrets?

Yoo Seon-yeop has gained a strong instructor!

Qing's eyes went dark!

Actually, it wasn't a situation that was so dark.

Even if he was a martial arts instructor, how can he teach the true meaning of a secret weapon just by throwing it at him?

In the first place, the semester at the Department of Political Science and Technology was not that long, and the intention was to teach the basics after learning them roughly.

So, an instructor, not a teacher or master.

Instructor, a public official whose job was to teach.

But Qing doesn't know. As always.

But, I guess Qing has never worked as an instructor and has never learned anything from an instructor.

When enlisting in the military in one's homeland, it was proper to write 'instructor' and read 'labor supervisor'.

The only concept that Qing knows about was school, and since it's for adults, it's probably something like a university.

Of course, universities were not educational institutions for adults.

But it was like that in Qing's hometown.

It's strange because if you don't go, you'll be treated strangely, and it feels like graduation itself was the starting point rather than in-depth and practical education in a single subject, so it feels like a school where you just go to become an adult.

And there were also virtues that a teacher should have.

Something for students! For students!

Not by the students, but anyway!

"Hmm. Is this it?"

Qing roughly grasps the basics of the sword.

Until now, I've been using the most perfect form of herbivorous technique through forced injection of martial arts, but it's really ambiguous when you just try to learn it.

First of all, the most difficult and challenging part was that I couldn't tell whether it was right or wrong to extend my sword like this.

Well, that's because what was said in the emergency report isn't accurate.

It would be nice if it were clearly written how to hold the sword, where the center of gravity is, what angle to maintain, how fast to swing it, and the position of the feet and hands.

But the text written on the emergency kit was like this.

Ilro, the road that runs from the Big Dipper to Zhongyuan, connecting the heavens and the earth.

Its course was like a falling star, but it leaves a deep impression like the builders who leave a trail. This was the work, the best of the five paths.

No, what does this mean?

What kind of road was this? Hey, Mr. Kim? Stop talking nonsense and just lay the road.

Nonetheless, Qing swordsmanship was quite powerful and seemed like a plausible herbivore.

Well, if you look at the passages that the bet passes through, you can roughly imagine which parts were trained and used, so if you focus on that and follow along, you can get a rough idea of the posture.

There were some pictures there, though they were woefully inadequate.

Well, it would be perfect if there was a video so I could watch and follow along. As for pictures, maybe one before, one after, and one after, but that would be a huge help.

Oro Sword Technique.

It looks like it was made up of five sword paths: downward slash, diagonal slash, left and right slash, horizontal slash, and stabbing, each holding one of them. It was called the five paths, oro.

And the ones who continuously execute chain attacks by connecting these five sword paths were the beginners.

In fact, Qing was already a master of the flower painting.

It means that even if you just hold a sword and swing it roughly, you were the owner of a destructive power that can cut down anything with a single blow.

Moreover, since the swordsmanship techniques I possess were already thoroughly familiar to me, at first glance they appear to be excellent swordsmanship techniques.

But then, isn't this not the Oro Sword Technique?

It's just a form of the Oro Sword Technique, and I don't know if it's the proper form or not, but it's just a Moon Sword and a Baekpal Sura Sword with a different outer packaging.

Something, um, this isn't right.

Shouldn't we properly understand and teach the basics, and not teach the basics that have been modified in our own way?

Besides, if I did it my way, there wouldn't be many people who could follow suit in the first place.

Since Qing's swordsmanship was based on his incredible physical abilities that surpass those of humans, wouldn't those lowly beings most likely end up with damaged muscles and dislocated joints if they tried to follow him without caution?

Something, something.

I wish I could get proper instruction from someone who knows this swordsmanship well, rather than just a beginner.

In fact, that was how external training was done.

The part that needed to be properly taught by a master was this external technique, the method of extending one's hands and feet and swinging one's weapon.

Even if you learn the internal energy method by just reading the book, it was not that difficult.

If you try to turn it around in your own way and think, "Oh, this was going to be a big problem," "I feel sick," or "I'm in a bad mood," stop right away and change the path your bet was taking. Sometimes, you make a mistake, vomit some blood, waste some time to calm your upset stomach, and eventually, you'll find the right path.

Of course, limited to Jeongjong's martial arts.

If it's magic, it doesn't end with just lying down. If you learn martial arts incorrectly, you could end up running around the mountains like an animal, eating people.

I guess I should ask the elder Dagger Sword Commander something.

But you were very busy.

And what was that look in his eyes? Should I say it's relief, or anticipation? I feel a bit awkward saying I don't know…

Well, was anyone there?

Is there anyone I can ask for some advice on my training?

"Oh! Sword Wu! You were training? As expected of Sword Wu! Well then, let's hang out together sometime!"

And then, Nan-Gong Shinjae immediately throws down his bag and takes out Nan-Gong Sega's special black iron wooden sword.

Arriving and immediately going straight to training without even unpacking or checking into a room was truly a swordsman-like action.

Qing's eyes flash open.

If you say Jo-Jo, Jo-Jo will come, if you say Tiger, a tiger will come, if you blow a flute, a snake will come out.

A character who appears very naturally and at the right time!

"What, was Geumwoo also a leader?"

"Then, if the author's swordsmen were determined to learn the sword and form a swordsmanship, how could I turn down the opportunity to work with such fierce swordsmen?"

Somehow, I feel like the condition has gotten a little worse since I last saw it.

This was because the Sword King Nan-Gong Daero, who prevented the worsening of Nan-Gong Shinjae's sword teeth symptoms, was away.

Of course, Qing doesn't know.

How could I possibly know the circumstances of another person's family?

Rather, how appropriate a time as this!

"Geomwoo, do you happen to know what Orogeomgyeol is?"

At that, Nan-Gong Shinjae shows off his pure white teeth and smiles brightly.

"Well then. Don't you know? It's a martial art created by the Absolute Sword Master about two hundred years ago."

"Absolute Swordplay?"

Qing tilted her head.

That's a really cool nickname, but I don't remember hearing it before. What was it, was it Lee In-ja?

No, but usually, it's famous up to the second person?

No, usually even the second person was famous!

Was it perhaps the third person?

Nan-Gong Shinjae, who saw Qing's 'expression', adds an explanation.

"Ah, the Absolute Swordsmanship Club, I'm talking about the swordsmanship club that existed in the Mang. It was a gathering of renowned swordsmen who made a name for themselves throughout the martial arts world. Well, I heard their initiation ceremony was a bit harsh. But then, the person who would later become the Great Emperor of Mucheon joined."

Nan-Gong Shinjae shook his head and continued speaking.

"It disappeared like that. What a shame."

It was a legend of a man who was beaten like a dog and even had his meeting sign taken down after showing off to a new employee.

"It was the result of a group of renowned swordsmen at the time declaring their intention to create a swordsmanship that encompassed all five of the most fascinating aspects of the Gangjung Yu Gwae Byeon. Isn't it fascinating? I applied to view it before, but it just wouldn't grant permission due to the entanglement of various swordsmen."

The swordsmen who participated together, as Nan-Gong Shinjae put it, all of the swordsmen became co-authors, so he gave up because he couldn't get permission from each and every one of them.

His expression brightened at that.

Anyway, the fact that you came as a leader means that you were a cadet of the academy, and since you will eventually learn, it also means that it was not a problem to do some advance study.

"Oh, Geomwoo. Does that mean you're interested?"

"Then! Are you saying that!? You're interested too, aren't you? Geumwoo! No way?"

"Yeah, here's the emergency!"

"Oh! As expected from Geomwoo!"

"Then, between the two of you!"

As Qing raises his sword, Nan-Gong Shinjae, in excitement, meets his wooden sword and crosses them.

Also known as the swordsman, it was something only for swordsmen…

"Actually, I came here as an instructor?"

"What!? You?"

"What? What does that mean? That incredibly unexpected reaction?"

"Hmm. Geomwoo was a true master of the Rising Sword, so he deserves that title, but…"

"What? Why were you trailing off?"

As Qing narrows his eyes, Nan-Gong Shinjae coughs and changes the subject.

"No, how serious am I? Can't you see this?"

"Why was that? It's a flute."

"Yeah, I'm telling you this was it?"

"……?"

Nan-Gong Shinjae couldn't understand where the flute and sincerity met and connected.

But for the roots of Qing Dynasty and the Korean people, this was a very important matter.

Daily hanbok! And the flute!

Truly the most feared symbol of a master!

Why would Qing have bothered to bring along a heavy, dusty, and rolling bag?

The teacher with the flute was a symbol of strictness, and he was the very embodiment of Qing's determination not to show a soft side as he took on the role of instructor of the boys' department of the Yizheng Martial Study Hall.

Of course, that fearsome boy instructor was wiped out before he could even begin.

"Anyway. I heard you're going to teach the Oro Sword to the trainees this time, but it's not easy to learn just by looking at the secrets."

"Ah, so that's what's been decided? Well, it's a shame to leave this swordsmanship locked away in the library."

"Hmm. I heard it's still unfinished?"

"That could be true. Saying it uses five principles also means there's no central principle. Come, let's not just talk about it. Let's see! Let's see the secret, the secret!"

Nan-Gong Shinjae shouts as if he can't stand it any longer.

Nan-Gong Shinjae's eyes, which were about to be examined, flashed with a mad light.

From the perspective of a backpacker rolling around on the ground, you might think that you should unpack your luggage first.

Well, it's reassuring to have a black raincoat.

When it comes to swordsmanship, Nan-Gong Shinjae was the brainy one.

As for swordsmanship, there were swordsmen as good as Geomwoo, well, swordsmen above Geomwoo were very common in Zhongyuan, but not swordsmen.

Is there no peak as intense as black rain?

Is there no sewer as good as Geomwoo?

In other words, it was difficult to discuss intelligence outside of the field of swordsmanship.

Well then, what would happen?

If the body was strong, the head was at ease.