\chapter{The New Semester Has Begun (15)}

It was a sight to see a tall, grown woman hugging the waist of another tall woman and lifting her up in a flash.

There, the sound of birds chirping and then the painful gasp of breath just before suffocation would repeat itself.

If Ximen Surin saw this, she would wonder if her disciple had finally turned mad, if her disciple couldn't tell the difference between what to show and what not to show in front of people, and if she should become a nuclear warhead itself that would descend at the speed of light with a stern voice.

Unfortunately, Ximen Surin was not here.

And in fact, it wasn't that embarrassing.

The sight of women joking around and making noise was not something that other people would find unpleasant or ugly.

Rather, they looked at it with pleasure.

Ximen Surin would say that this very perspective was the problem. Are women really just a being who frivolous play and flirting with each other?

It was around the time when Qing arrived at the banquet hall.

Laughter was very physically demanding.

You will know if you just keep for half of half ke (about three minutes) right now.

Laughter was a truly brutal full-body exercise that used all the muscles in the body, strained the respiratory system, and placed a huge burden on the body's circulatory system.

So, Sima Chunfeng, whose martial arts skills were only first-class, was already exhausted.

Her abs were aching as if she had swallowed an egg, her whole body felt heavy as if she had swallowed water, her throat was sore with every breath, and her voice was already hoarse, so every breath she took was mixed with a wheezingg sound like an animal.

"Sima-lang? Aren't you going to eat? Do you really not want to eat with me that much?"

"Bon, Sima-lang, geuh, I don't support you- kkaheuk."

Then, suddenly, Sima Chunfeng's shoulders sagged.

\textit{Oh my, is she dead?}

Qing, startled, pokes her side.

Then she flinched, thankfully there was a reaction, so Qing thought maybe she had fainted, but now it seemed like she had just reached her physical limit.

Qing reflected a little, holding Sima Chunfeng, who had fallen down again.

\textit{Hmm. Was that a bit harsh? But it was fun.}

As Qing muttered that, she started to squirm, huh? There was no response at all, but she kept squirming.

"Heehee, heehee, stop, that little……."

"Are you going to eat dinner?"

That was when.

Qing suddenly felt a heavy gaze.

I turned my head.

"Young Lady Ximen…? Why, only to Wisdom Flower? Me too, me too…? Even though you promised."

Qing's eyes met with Mo Yong-ju-hee's, who was muttering with a pitiful look like a puppy that had been drenched in rain, and , whose small face was especially large and whose eyes were filled with tears.

"Huh? Young Lady Murong? When did you get here?"

"Around the time you hit that arrogant test taker in the back…"

For some reason, Murong Zhuxi was extremely gloomy.

By the time Qing hit Chai Sengxia, lunchtime had already passed, so she must have been there and watching. She seemed upset that Qing hadn't noticed.

"Hoo, hoo, Heavenly Blossom Sword, hoo, if you want it so, hoo, so desperately, hoouk, this one time, Sima-lang, hoo, I have to give in- ugh."

Sima Chunfeng, who finally gave in and refused to admit defeat even if she died, collapsed to the ground in an instant.

After all, Sima Chunfeng who was held like a scarecrow, was already on the verge of exhaustion, so the moment her waist was freed, she would have just been dropped in an instant.

Qing spread her arms wide.

"So, Miss Murong? A reunion hug?"

"Ahh……! Yes……!"

Murong Zhuji, who had blossomed in an instant, threw herself fiercely towards Qing.

It was an unexpected intensity.

\textit{I thought you'd just come and give me a hug, I didn't know you'd actually fly in with open arms.}

\textit{Why, the flying squirrel that used to hug me back home? Is that really a flying squirrel? Anyway, just like that?}

\textit{It seems that Young Lady Murong was much happier than I thought.}

Since there was nothing she couldn't do, Qing hugged Murong Zhuji and twirled around and around.

"Hehehe……"

Murong Zhuji smiled and giggled.

\textit{What the heck, it's just at the level of Ciyu? Is this okay?}

\textit{Of course, Young Lady Murong is is closer to a child in terms of height.}

Beneath her, Sima Chunfeng, who had fallen into the swastika pose, thought. No, she wasn't the type of person who merely thought, so even with her gasping breath,s he managed to squeeze out a dying voice.

"Ugh, it's too much. Heavenly Blossom Sword, after inflicting so much relentless pain and gaining concessions, you're doing this to me right then and there. But, yes, this cruelty and ruthlessness are also aspects of genius. In terms of cruelty and ruthlessness, I'll count it as Heavenly Blossom Sword's victory."

But cruelty and ruthlessness were never considered virtues, so even if you win, it won't be considered a praise…

Whether Sima Chunfeng said it out loud or just thought it to herself, she herself couldn't even be sure because she just closed her eyes and slumped down.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Youth Division of Yizheng Martial Study Hall was only called a youth division in name, but strictly speaking, it was not a youth division.

To be precise, it should be said that it was close to aristocracy or the nobles.

Because it was a social gathering for young people who have entered the martial arts world through recommendations.

Considering that the original purpose of the establishment of the Yizheng Martial Study Hall was to be a seasonal training camp for the boys and girls of the Orthodox Wulin world to form relationships, this could actually be said to be closer to its essence.

So, does that mean that talented children could not enter Yizheng Martial Study Hall?

Of course, the Wulin Alliances's handling of affairs was not that sloppy.

So, even though they were boys and girls, they were scheduled to train with young people in a regular training center, not in the boys' department.

In the interest of attracting talented people to the Orthodox Wulin, it was easier for young people to get into debt than an estavleshed sect's youngster, and their future was also bright.

You might say that the intentions were too mean and calculated for an Orthodox Wulin event.

The Wulin Alliance was merely an interest group of Orthodox faction, not a charity organization.

Anyway.

Zhuge Xiang, a descendant of a noble family with a long history of participating in the Yizheng Martial Study Hall's Youth Division for generations, was now facing a truly nerve-wracking opponent.

"Oh, hello? My name is Xiang."

In front of, Ciyu's dull eyes take in the image of Zhuge Xiang.

Adults might only thought that the child looks really lifeless, with dark bags under her eyes, and that she looked really tired.

But from the children's eye level, Ciyu's pitch-black eyes, like a bottomless pit, were quite a frightening sight.

"Who."

"Oh, so, I'm going to be your mother?"

A wrinkle appeared between Ciyu's eyebrows.

It was an expression she learned from watching her Cold Mother.

Zhuge Xiang flinched at that.

Although Ciyu was always looked cute to Qing, she had a rather cold and intimidating aura to her peers.

It was also a ghostly aura that came from countless accumulated murders.

"But you're a kid too."

It was Ciyu's counterattack that Xiang was too young to claim to be her mother.

Even though she was already used to her father(?) calling every woman she knew 'mother' after experiencing it many times, she felt a bit of resistance to Zhuge Xiang.

"But, uh, I'm Gege's, that is, Ximen Gege's concubine…?"

"But you're a kid too."

"No! Originally, it is okay to have a concubine! The Taishigong Shu\footnote{'Records of Grand Historian', or Shiji, written by Sima Qian} even said that there were many concubines younger than the children."

It may be surprising to hear this, but in reality, there were many folk tales in Zhongyuan, such as the ridiculous fights between the adult children and the younger concubines, or even forbidden love.

However, Ciyu tilted her head.

Because, no matter what book name was mentioned, Ciyu had not even been able to read the Thousand Character Classic.

"What is a concubine?"

"Huh? A concubine, you see? She's a wife. A woman of low rank. Strictly speaking, she's not a wife, but a concubine. Hmm? Why is that?"

"…? What are you talking about?"

"According to the Book of Rites, 'the Emperor has six kinds of wives: a queen, a wife, a concubine, a concubine, a wife, and a concubine, and they were called the Six Palaces'. In the Book of Rites, it was recorded that the Emperor has six palaces: three wives, nine concubines, twenty-seven concubines, and sixty-one concubines, and there was no limit to the number of concubines. Furthermore, according to the law, the feudal lord has nine wives: four wives and five concubines. Furthermore, 'A man who has only concubines but no wife was considered unmarried, and his household title still belongs to his parents.' Now, do you understand? Ahem."

Zhuge Xiang pretended to be a savvy.

Usually, by this time, everyone would be amazed by Zhuge Xiang's intelligence and showered her with praise.

Of course, Ciyu doesn't know.

"…??? What are you talking about? So what's a concubine?"

"Huh? A concubine, so, a concubine?"

Actually, what would Zhuge Xiang knew about the world?

She read books (a lot of them), but the world was just inside the high walls of the Zhuge family.

The famous fights and discrimination between wives and concubines usually did not occur if the family was too wealthy.

This was especially true for the mothers of the Zhuge Family, who had a sense of camaraderie similar to that of female warriors.

So Zhuge Xiang didn't actually knew what a concubine either.

\textit{What's the difference? Our mothers were very affectionate towards each other, right?}

\textit{I understand that the wife was superior and the concubine was inferior, right?}

In fact, the extent to which Zhuge Xiang knew was just that much, so the basis for her decision to become Qing's concubine was probably because the two didn't seem to have much of a difference.

"Well, then, what is a concubine?"

"I asked you first."

"Then, let's go ask the adults."

Everyone has something they can't stand.

When Zhuge Xiang was curious, she couldn't hold back.

Fueled by her unique curiosity, she had the courage to act quickly and run towards things, and unlike before, she has shown no signs of difficulty to takes the lead by grabbing Ciyu's wrist.

Ciyu pretended not to be able to win and followed behind, looking down at the small hand guiding her arm.

So, two mischievous children appeared in an empty building while taking a test.

"Ah, Sir, Sir."

"Oh, it's Xiang'er. And with Ciyu? You two are already together?"

"Yes. That's right. Sir. This Xiang'er have a question."

"Yes. The duty of a wise man is to inquire. That's a wonderful attitude. What are you curious about?"

"Hehe."

Zhuge Hyang, an expert at cutesy, let out a charming laugh and immediately asked a question.

"What is the difference between a wife and a concubine?"

"Pffftt."

"Even in the Book of Rites and the Code of State Law, it was said that a man may have multiple wives, placing concubines on the same level as wives. So why are wives considered noble and concubines considered lowly? Why aren't concubines considered wives, even though they live together? Why?"

"Uh uh. Hmm. Um."

Sima Junsafo, Chunfeng's uncle, was sweating profusely.

\textit{What is this situation?}

\textit{Could it be that this child has already awakened to the cunning of the Zhuge Family and is trying to trap the Sima Family?}

But Zhuge Xiang's eyes sparkled.

Half bright, half curious, half innocent.

The Heavenly Blossom Sword's adopted daughter, who was holding hand next to Zhuge Xiang, had a somewhat rotten look in her eyes, but she was still looking up at him as if she was also curious.

"Uh, um. Oh, something urgent all of a sudden! Oh no! Sorry! There's some paperwork I didn't get around to taking care of!"

Sima Junsafo's choice was to flee.

Of the Thirty-Six Stratagems, the most effective one was the retreat. If there was no gain from fighting, it was best to run away immediately.

"Oh, it's Monk Weifeng!"

"Amitabha, aren't you the Young Lady of the Zhuge family?"

"Venerable Monk, Venerable Monk, what is the difference between a wife and a concubine?"

"Amitabha, um, Amitabha. Hmm, um, Amitabha. So, this Monk has already severed his ties to the secular world? Yes, that's right! This Monk has severed his ties to the secular world. That's right. This Monk doesn't know about that exact part. Then, next…"

Weifeng was moving back in a mysterious manner, still in his standing position, and disappeared without a trace.

Zhuge Hyang's eyes burned brightly.

\textit{Is this really that hard? Then I'll figure it out!}

"Ah, Master Cheon Yu-dan!" "Master Seo!" "That's! Master Gyeong, right?" "Master Seo Seo-go!"

There was a reason why she was called Zhuge Family's Young Genius.

Zhuge Xiang could recognized anyone she met just once like a ghost.

So, the victims kept piling up.

In the end, the two of them were unable to find an answer.

As Lao Tzu said, we should live purely like children.

It also means that it was not right to tell a child something that was too embarrassing to tell.

So, outside, they were busy with exams, and inside, the adults who heard the news of the appearance of a pair of a troublemaker were sweating profusely as they tried to avoid them.

Entrance exam day one. End.