\chapter{The New Semester Has Begun (10)}

It was a first test where tension was growing.

The problem was that the atmosphere was tense because you had to watch the test tube and go to the test stand.

That was the moment.

A young man steps forward.

A rather relaxed expression, light steps.

A pretty and beautiful appearance.

Why, there's a guy like that. The kind that naturally attracts attention. You could call it the atmosphere.

Actually, he's just handsome.

Originally, handsome men and beautiful women were welcomed and liked just by their presence, and so they were brimming with confidence, and the composure that came from that confidence tended to capture attention.

The freedom that comes with that kind of confidence was again gained by winning favor with confidence, and this confidence rises again, and so on, and it was in the cycle of infinite favor.

Of course, does it really matter if the guy was handsome?

There's a new kid. He's a bit picky.

"I am Cai Shengxia, the current successor of Azure Dragon Gate. I would like to ask you for a favor."

Azure Dragon Gate. Isn't that a pretty cool name?

She immediately asked the person sitting next to her, Wisdom Pouch, or rather, Sima Chunfeng. Because curiosity can't be contained.

"Sima-lang, is Azure Dragon Gate a famous sect?"

"Ugh, what the hell, Heavenly Blossom Sword. Are you asking me, Sima-lang? Of course, ignorance was nothing to be ashamed of, and it's only natural to seek wisdom from this Jinang Hyeonhwa."

And then, for some reason, Sima Chunfeng, who was very proud, continued speaking.

"Heavenly Blossom Sword. They say Zhongyuan are vast, and the eccentrics are as numerous as the stars in the sky and the grains of sand on the beach. In Jianghu, anything can happen without surprise. Sometimes, disciples emerge from masters who have turned their backs on the world and lived in seclusion, and sometimes, because they live in rural areas, young masters who were unaware of their exceptional talents were bound to exist. That's how it is."

"Oh, a hermit."

Qing nodded in understanding.

\textit{Hmm? In the end, isn't that saying that you don't know either?}

\textit{Why do you raise your chin as if you're dispensing knowledge?}

"No, I asked you to explain about Azure Dragon Gate."

"Heavenly Blossom Sword. They say Zhongyuan are vast, and the eccentrics are as numerous as the stars in the sky and the grains of sand on the beach…"

Somehow, the same answer came flying back, without a single word or intonation changed. If it were back home, she'd wonder if there was some kind of built-in recording function.

But the latter part was a little different.

"…is inevitable? Countless such wisdom exists in the world, but unfortunately, as the youngest deputy commander of the Wulin Alliance, which protects the peace of Jianghu, I, Sima-lang, have made the magnanimous decision to only take the wisdom necessary for the peace of the world. It's truly a shame for the wisdom that has gone unnoticed by Sima-lang, the world's greatest brain."

In the end, she said she didn't know.

Qing decided not to ask again.

\textit{What is this, the wisdom pouches is huge, but its inside is really messy.}

\textit{But isn't that enough? Isn't it enough to just posses wisdom pouches? Indeed, it is. At that level, its mere existence is valuable. It's the largest and most natural form within the acceptable range of human perception. Is it a World Heritage Site?}

"Where are you looking while nodding?"

"Yes, yes. Indeed. The best in the world. I'm surprised once again."

"Haha, now you see the true value of the Sima-lang? The Sima-lang you've met is…"

As the duel began at that time, Qing naturally ignored Sima Chunfeng.

This time, the examiner was White Tusk Sword\footnote{白牙劍} Wu Zhangyue\footnote{吳長樂; Oh Jang-rak in the original text}, and he seemed to be the leader of a combat team in the Wulin Alliance.

As his nickname suggested, he was a man with exceptionally bright white teeth. In fact, his teeth were so dazzling that Qing couldn't even hear his self-introduction properly.

Giving the first move to the applicant was as natural as the rising and setting of the sun and the moon.

Cai Shengxia's feet touched the ground.

Rather than moving forward, he lightly tapped his toes, picked up speed, and then, what the heck, he spun around, arms outstretched and swinging briskly, he picked up speed.

In fact, a lowly person should not dare to turn around in front of a high-ranking person.

Even if it's just for a moment, the act of exposing your own back clearly revealed your weakness.

On the other hand, the human neck surprisingly doesn't turn that well, and there were no eyes on the back of the head or the back, so when you turn your body, you lose sight of the enemy.

You couldn't see the enemy, and the enemy could see you weaknesses clearly, so if you tried to attack half-heartedly, you would most likely get stabbed in the back and fell.

On the other hand, you could use the rotation as an axis to deliver a powerful blow.

In that respect, it could be said to be a fairly strategic choice.

Since the examiner would give you the lead anyway, you could prepare for an attack with all your might from the start without worrying about a counterattack.

Since this was a request to maximize the applicant's strengths, was there a knack for judging the situation and using it to your advantage? When I think about writing an evaluation like that—

"Oh!"

Suddenly, exclamations of admiration burst out here and there.

Regardless of whether you were in the judges' seat or in the audience.

Blue energy swirls from Cai Shengxia's toes, taking the form of a gentle whirlwind and wrapping around his body.

With the wind of the dragon slowly sweeping around him, Cai Shengxia raises his sword and turns his body, stretching out his limbs and swaying them, sometimes stretching them out in a controlled manner and sometimes folding them gently to draw large and small curves.

It looks more like a dance than a proper martial art.

Why, was it called a dance line?

The long limbs stretch out vigorously, making it powerful and intense, unlike the dance style that emphasizes only the softness of Zhongyuan.

A sight that somehow reminds me of my hometown.

Should we say this was timeless?

Unlike the young people who were immersed in untimely nostalgia, the expressions of those with true discernment, the experts in their seats, were full of surprise.

The dragon swirl that surrounded Cai Shengxia was a vague shape, but it was also a blade with clear killing power.

A blue stream that wrapped around his entire body, his limbs, and torso, a dragon-like wind that wrapped around his entire body, and a light green stream that flowed along the blade and formed the shape of a larger greatsword.

Three streams of energy, each with slightly different properties, swirled together in the form of wind.

Above all, it was the flow of energy.

The wind blows from all directions of heaven and earth and takes the form of a flow, so it was not just the wind, but the energy of nature flowing together.

An amazing skill that uses not one's own internal energy, but the energy that exists in nature, the energy of nature itself!

The expression on Wu Zhangyue's face was heavy.

Wu Zhangyue clenched his teeth to hide his frustration and was busy swinging his sword energy like a net in all directions to block the storm.

The sound of iron hitting against metal was loud.

It was like countless blades of wind swirling around.

A man cannot catch the wind.

Also, no matter how much a person's internal energy was overflowing, it cannot exceed the energy of heaven and earth.

In the end, it seems that Wu Zhangyue had come to a conclusion.

A white starlight shone upo Wu Zhangyue's sword. It was a sign of someone who had surpassed the limits of human achievement.

The sharpest sword Qi of all time, Sword Force.

Cai Shengxia's dance moves also changed accordingly.

The intensity diminishes, the tempo slows down, and the dance moves more gracefully, creating distance.

On the contrary, the wind current swirls more violently, and then rushed towards Cai Shengxia's sword, forming a gigantic wind greatsword.

It was a dense flow of wind so clearly defined that the blade was not visible at all, a concentration of natural forces.

Wu Zhangyue kicked the ground first.

It was a moment that everyone will remember.

Because the first strike belongs to the hasty.

It was decided that giving more time would be disadvantageous, so anyone who knows the law will understand who has the upper hand.

Even if you don't know, it's a realm of intuition that can be known just by looking at the expressions of Cai Shengxia and Wu Zhangyue, the carefree young man and the anxious examiner.

And oh my!

Soon the wind sword and the strong energy clash.

And. Two people crossing each other.

Silence falls over the two people who have turned their backs on each other.

The eerie starlight and the wind that enveloped the room disappeared as if they had never existed.

Everyone held their breath and watched the end of the clash, and there was only silence in the arena.

Finally, Wu Zhangyue opened his mouth.

"What is the name of that martial art…?"

"It's called Azure Dragon Dance."

"The Azure Dragon Dance. Indeed. It is a divine art worthy of its name. I… am defeated."

After saying that, Wu Zhangyue staggered while vomiting blood.

-Wow!!!

Suddenly, a loud explosion comes out, as if the earth was shaking.

This was truly an unprecedented event!

The test taker beat the examiner!

"It is truly Azure Dragon, the Young Azure Dragon!"

"Young Azure Dragon!" "Young Azure Dragon! Young Azure Dragon!"

Starting with someone shouting in admiration, the crowd cheered loudly, repeatedly chanting for Young Azure Dragon.

It was truly the birth of a young hero.

\textit{Hmm, what on earth is this atmosphere? Why all of a sudden?}

There was even a word from Sima Chunfeng, the person sitting next to me.

"As expected, Young Azure Dragon. This year's Yizheng Martial Study Hall's term will be truly entertaining. I'm looking forward to it. Hehe. Is another archrival making an appearance?"

What fun would it be if a skilled person entered?

Well, I think it would be fun if they created something like a dance club.

"No, with that level of skill, why did he apply to Yizheng Martial Study Hall?"

"Heavenly Blossom Sword. They say Zhongyuan are vast, and the eccentrics are as numerous as the stars in the sky and the grains of sand on the beach…"

\textit{What is it? Is it some kind of talking doll that you press on?}

\textit{It's like they're playing real recorded lines?}

"…turning your back on the world and living in seclusion-ack!? What, what are you doing?"

Sima Chunfeng let out a sharp scream when her side was poked.

"No, I thought that if I pressed it, the dialogue would start from the beginning."

"…? What are you talking about? Heh, as expected of the Heavenly Flower Sword. Yes, there are aspects of it that were incomprehensible to us divine beings. So, where did we end up? In any case, a hermit is unaware of the world's circumstances, of his own realm, or of the ignorance of the world's people. So, I, too, must not know the extent of my own power."

"Ah. I think I know what that feels like."

Why, don't you feel that way?

The strict teacher, in order to warn his disciple against arrogance, said that his realm was only between third and second rate, but in reality, he was already a top-notch master.

And even after the disciple came down, he thought he was weak and did something like that?

"Also, studying at the Yizheng Martial Study Hall is not only a learning experience, but also a golden opportunity to make a name for yourself in the martial arts world. Wouldn't a young master like that naturally want to join the Yizheng Martial Study Hall of Sima-lang and make a name for himself?"

It was not known when Yizheng Martial Study Hall became Sima Chunfeng's, but other than that, it was not a completely wrong statement.

By the way, Azure Dragon Dance.

Qing seeked info from the Martial Arts Window, which she used only when she feels most comfortable.

\textit{The results aren't showing up, so is this one unfinished?}

\textit{Anyway, this Martial Arts Window is only good on the surface, but it's no help at all. It's useless.}

The loyal Martial Arts Window might felt so unfair that it's about to break and a blue screen will appear.

Qing's eyes narrowed.

\textit{But Azure Dragon Dance. Azure Dragon Dance.}

\textit{There was something on my mind.}

\textit{If it's Azure Dragon Dance, are there any others? If so, isn't the Black Tortoise a bit disappointing? There should be Azure Dragon Dance, Red Fenghuang Dance, and White Tiger Dance, but Black Tortoise Dance is a bit unique, and its name is abit lacking. Black Tortoise Dance. Black Tortoise Dance. Hmm, if it's the Turtle Dance, it might be a bit funny, right?}

Well, that was exactly what Qing was thinking.

Originally, Qing didn't have any particular thoughts.

It's not like she have any particular faults with his bad karma.

As Chunfeng said, the martial arts world was vast and the population was bustling, so the number of martial arts skills was also diverse, so it wouldn't be a big deal if a new skill popped up somewhere.

So she guessed that's just how it is.

But it seems that Cai Shenxia had different thought.

Even after finishing the exam with flying colors, he didn't back down and stayed in his position.

The crowd's cheers also died down at some point, and their eyes sparkled as if he was trying to show them something else.

Of course, it was currently the entrance exam period, not the grand stage for Young Azure Dragon's Jianghu debut.

One of the examiners cautioned.

"You should step aside, Young Expert. We need to take the next applicant."

But Cai Shengxia only answered with a faint smile.

"Before that, I heard a rumor that a great swordsman, who is expected to be the Greatest Under Heaven in the future, is here. I would like to ask for her guidance, even if my skills are limited."

Exclamations of 'Ohh' erupt from all over.

At the same time, everyone's heads turned and the entire exam ground's gaze turned to Qing.

It was an extremely burdensome situation, with people crowded around looking up with sparkling eyes full of anticipation.

Qing tought to herself.

\textit{You want fight me?}

\textit{Hmm. Why me?}