\chapter{The New Semester Has Begun (2)}

Qing doesn't know the person named Wen Feihou.

In the past, he was evil according to his family, but suddenly repented and wandered around doing good deeds.

Or, as the eldest son of the Sapha family, he accumulated a lot of good deeds while acting as the sole restraint, and then he went out and did bad things and ate away at them, which was the result of his current number.

There was a rough idea of the principle of karma.

I don't particularly like the numbers that judge people by mixing utilitarianism and consequentialism.

But isn't that why it's trustworthy?

It may be reasonable to make a strict and inhumane evaluation based on a certain standard, regardless of the person's circumstances and kindness.

So, at the very least, we can, or should, give the person wearing Qing number right now a chance.

Qing, who had gathered her thoughts, opens her lips.

"Young Expert Xiao."\footnote{蕭小俠; Xiaoxiaoxia}

\textit{Now that I say it, Hmm, it's a bit strange.}

\textit{When I say 'Xiaoxiaoxia'\footnote{Small Small Expert}, I think it's referring to a really small person. But calling him 'Xiaodaxia'\footnote{Big Expert Xiao} was also a bit odd.}

\textit{Then, if it's a Xiao Xia, can we call it a Xiao Xiaoxia, and if it's a very young Xia, can we call it Xiaoxiao Xia?}

"I've already heard that the Wen Feihou here has already cut ties with his family. Just a moment ago, the crowd here jeered and criticized him. Isn't this a bit harsh to resolve your family's grudge when he's resolved to sever ties with that unjust family, even if it means enduring the humiliation"

"That bastard! He was born, raised, cured, consumed all kinds of elixirs, and even mastered martial arts. All of this was stolen from his family, from our household! What, what's so cruel about it!?"

Xiao Yindiao's voice trembled with anger.

Still, for someone who was upset and angry, Xiao Yindiao was quite logical in his words.

"And what? The Yizheng Martial Study Academy? If that kid becomes a master, won't it only benefit his family? If he shuts up about everything he's been doing and pretends to be a good person because he produced a master of the political faction, then you're a piece of shit, you piece of shit!"

Well, as soon as I think about it, shit comes out.

Actually, Qing agreed with what Xiao Yindiao said.

If you think that I will see it because I came from a family, then if you cut off the person you want to save and send him away, then there will be no end to the resentment. Isn't that right?

Besides, even if you say that he was born into that kind of family and there's nothing you can do about it, he was originally not in good health, but he survived and took all kinds of elixirs, didn't he limp and run away like some third-rate warrior?

It was really amazing, but I wondered how much of a good elixir could a wealthy city breakwater, even if it was the first time I heard of it, could have obtained.

Qing looked down at Wen Feihou.

It meant to ask if there was anything to say.

"Uh, that's why. I, I'm sorry. Uh, so, since I was born? Because I used up your family's fortune?"

He suddenly looks down at Wen Feihou with a murderous gaze.

"Is that all you have to apologize for?"

"Uh, I didn't know that my family's prosperity was intertwined with yours, and since I've already cut ties with the family, should I be the one apologizing for that? If I'm going to apologize, I think the head of the family or my grandfather should be the one to do it…"

"Are you refusing-"

"No, no, no, that's not it. That's because, you're trying to get revenge, and I can't apologize on behalf of my family. I haven't heard anything about them lately, but if Young Expert Xiao is acting like this, it seems like they're still doing some reckless things. If I apologize for my family's evil deeds, it'll end up looking like the Wen Family has apologized, right? Something like that. It doesn't benefit you if I apologize on behalf of them, so I can't do that."

Although it was a redundant statement, it was clear what kind of person Wen Feihou was.

If he were to apologize here on behalf of his family, the stakes that Xiao Yindiao could claim in the grudge against Wen Family would be reduced.

Anyway, we apologized.

"It's not that I'm not at fault. I'm, uh, representative, not on your behalf, no, so, uh, um. Atonement? No. That's right, qualification, between Wen Family and you, I have no right to say anything, right, I'm not qualified, am I?"

"You bastard……"

"Well, you said that I lived off the money they stole from your family, so if I somehow manage to pay back the money they stole, how much do you think I should pay you back?"

Then, ahduk!

Xiao Yindiao made a rough, grinding sound, then turned around with a flushed face.

And then it starts to walk away slowly.

The crowd that had gathered dispersed here and there with expressions of being exhausted.

Among them, the man who had hung himself with a sword during the chase after Onbi looked somehow familiar. I couldn't help but think, "Ah! Nyangyacha! A candidate for Nanhwa's husband!"

But since we've only seen each other a few times, and since Mr. Yura Dal's old man hasn't given up yet, maybe he could become the husband of the disciple of the Divine Maiden Sect?

It was the moment when Qing was about to extend her hand, pretending to know something.

"oh my……."

A groan.

Wen Feihou's shoulders drooped, as if he was finally starting to relax a bit.

Then, he made a sound as if something had occurred to him.

"Thanks to your help, Great Expert, I was able to save my life after facing this grudhe! I am grateful for your life-saving grace!"

I bow politely and offer my greetings.

What's up, Qing?

"What about the grudge?"

"Since I have cut ties with my family, I think I should also cut off my surname… So I thought I should just go with the most common one, Zhang."

Wen Feihou, or rather Zhang Feihou, answered like that and then quickly added.

"By any chance, Great Expert, were you headed to the examination hall of Yizheng Martial Study Academy? If it's alright, could I, or rather, could I, show you the way?"

"I'm okay."

Qing looks around.

Xue-i-ri shook her head slightly from side to side.

Chen Changming shook his head.

It's not just that I'm okay, but isn't the opinion of my companions important too?

Of course, Ciyu was still a minor and has no say. If she felt wronged, she should have been the guardian, not the ward.

Then, Zhang Feihou tells the story in a crawling voice.

"Uh, actually, I drank some mountain poison."

"Ah. So. It's a bit ugly, ah, on, no, I'm not saying that Jang So-hyeop was ugly."

"No. It might have been a little ugly…"

It wasn't a guide, it was a plea to please take me with you!

Well, now it's finally making sense.

It's said that the level of martial arts was reversed between the eldest son of a wealthy family and the son of a poor family.

Moreover, since the young man had drunk the poison, he would have been frightened and run away immediately when he saw the man chasing him with a knife.

"Well, I've already save you, so it's a bit much if you get stabbed after. Right, kids? Now, lead the way."

"Yes. Thank you! Thank you!"

The entrance examination room of the State Affairs Office seemed to be very busy preparing for the exam.

They must have been so busy that no one bothered to call and just closed the door.

I carefully pulled the door to see if it was locked, and it creaked open.

Of course, the only people who will be going in and out of the testing center before the test even starts were the officials, but even so, it's still like that.

In the vast training ground, laborers were busy carrying huge stones and iron plates.

What? Is it a release or a detention? Did I come to the wrong place? No, I followed the directions, so did Zhang Feihou get the wrong test site?

If I hadn't seen a familiar face then, I would have thought I had come to the wrong place.

But wouldn't a tall man, barely seven feet tall, hugging a thick iron bar and moving around be a very striking presence?

"Hey, Zhuge!"

"This voice, Sister!?"

Kwung! It was the sound of a heavy iron bar, a lump of iron close to a pillar, hitting the floor.

"It's been a while, Zhuge. I saw you last year, didn't I? Let's see. Did you get any thicker?"

"Normally, if I saw you last year, I wouldn't say it's been a while, Sister."

This was the atmosphere of Zhongyuan, the continent.

Because it was such a large landmass, if you saw it last year and saw it again this year, it doesn't count as a long time.

"Hello, Sister Xue. But I see there were more people in your group."

"This is Chen Changming, the youngest of the Divine Maiden Sect disciples, and personally, she's my younger sister. This is my daughter."

"Daughter? You mean your daughter? You must have gotten married by now, huh? And this person?"

The decision not to ask a deeper question was, as expected, the judgment of the person in charge of intelligence among the Half-Sword Double-Saber Association.

That's not something you should say in front of a child.

"This person here is applying for the entrance test."

"Oh, no. Applicants were prohibited from entering."

"Can't you put him somewher for a while, since he need time to detox after taking the mountain air poison? Oh, but what's the fuss about? What are all these rocks and iron bars?"

"These are the materials to be used for the basic skills test."

"Did Zhuge have to do it himself? No, no, I guess you just volunteered."

"As expected, you're sometimes brilliant, Sister! Indeed, wouldn't this be a good opportunity to train your muscles for combat?"

\textit{What do you mean sometimes brilliant?}

Myeongseok means clear and intelligent thoughts and judgments.

But doesn't being called bright sometimes mean you're usually stupid?

\textit{This kid, at some point he started to be a bit cheeky, but now he's becoming more and more blatant.}

"But, Sister, in fact, applicants are penalized the moment they enter or leave the exam room early."

"Oh no!."

Zhang Feihou, who had been standing there awkwardly, unable to join in the conversation, turned pale.

"Huh? Why? Then shouldn't you at least put up a warning sign?"

"No, it's not that. We didn't announce it on purpose. We wanted to penalize anyone who sneaks in to look around, or even if it's not an illicit request, tries to show off by offering drinks or snacks."

"Ah. So you left out all the suspects? Hmm, then isn't this a honeypot? Or not?"

"Honeypot, what a wonderful word! I think I know what you mean. Hmm. But this person has unavoidable circumstances, so he can pretend to be a laborer and leave before anyone finds out. Sweating, heart pounding, and blood circulating will speed up the detoxification of the poison, right?"

"Yes, thank you!"

"You can ask the people behind that door what to do."

After receiving the equipment, Zhang Feihou once again offered Qing a bow of gratitude and then carefully left towards the door pointed by Zhuge Lixian.

Zhuge Lixian was very natural in his usage of of manpower.

It's not just about being good at something, it's about getting people to do things for you.

In this regard, it was at a level where it can be upgraded to the level of a Xuega-nom!

"But why didn't you tell him not to go and tell anyone? Is this another honeypot?"

"Actually, there hasn't been a single applicant caught so far. Everyone's careful about their speech, so there's no way anyone would openly approach. That's generally the plan Sister Chunfeng comes up with. It doesn't work. Well, thanks to that, we've saved some manpower."

Qing was just called Sister, other women were called Sister with their surnames, but only Sima Chunfeng was called Sister Chunfeng.

If others heard it, they might think it was a special relationship, but Qing seemed to know the general reason.

She just don't like being called Chunfeng, so Zhuge Lixian kept calling her that.

It's a well-known fact that Zhuge Liang and Sima Yi were enemies.

"Is Zhuge also an instructor?"

"Ah! So you're here as an instructor? Well, it would be odd for a master of Unrestrained Realm to be just the group leader. But, are you okay with that? Hmm. Well, since teaching and ignorance are separate things, you might be surprisingly good at it—Agh."

Taak, Zhuge Lixian grabbed her forehead.

This was so annoying, I'm really annoyed.

It was just a simple finger flick without any nuclear power, so it didn't have that much destructive power.

"I'm not particularly confident, but I think I could be a good instructor for the Youth Division."

"You'reqoing to be the instructor for the Youth Division?"

At that, Zhuge Lixian furrowed his brow.

"Aren't you mistaken, Sister? The Youth Division's instructor has already been appointed."

It's been a long time since she's had that expression of ignorance on her face.

"Huh."