\chapter{The New Semester Has Begun (7)}

The crowd spotted a tall woman walking out of the State Council building.

She was wearing a veil.

The bulging parts were extremely excessive, and the waist, which was tied up tightly compared to the top and bottom, was thin, so it was definitely not a man's figure.

There were so many women wearing veils in the current Zhongyuan that it was a bit of an exaggeration to say that they would trip over their feet.

Because of whom? Because of the Heavenly Blossom Sword.

So the crowd gulped.

No way? Is that the Heavenly Blossom Sword himself?

"Hello, everyone. I am Ximen Qing, a junior martial artist of Jianghu."

And two beats later, a passionate shout erupts, shaking the hall.

"Heavenly Blossom Sword!" "Odubangjeong!" "Hangahyeonsin!" "Gangnam Beauty!" "Three Heads of Gain!" "The Most Beautiful in the World!" "Peek your face!" "Beep!"

Hmm. It's grown a lot in the meantime.

Gangnam Beauty, well, I kind of get what it means, but it feels a little off. Strictly speaking, is it closer to full-body plastic surgery? I don't know.

(Gangnam Beauty means a glamorous and gorgeous beauty, and is used in Zhongyuan to praise beauty.)

But which kid is that with a straight face? Anyway, there are some kids who think they can pretend to be cheerful and say whatever they want as long as they hide among people.

Just try catching one someday.

The greatest advantage of the cotton swab was that it didn't require any facial expression control, so the crowd couldn't see the blood-scented smile of the Cheonhwa Sword.

however?

"Whew!" "Wow, Heavenly Blossom Sword Sister!" "Awesome!" "Cheon! Hwa! Sword! Cheon! Hwa! Je! Il! Sword!"

What is this popularity? Am I this popular?

The atmosphere was not calming down, so Qing raised his hand to stop it.

Then the crowd's gaze is drawn to the flute in his hand, which is so white it could almost be transparent.

It was a truly ugly iron flute with a rough appearance and a dull, damp color, making it even more striking.

"Although my studies are still incomplete, I've been chosen as an instructor at the Yizheng Martial Study Hall and I would like to learn from you the candidates."

Then the test takers look at each other.

Heavenly Blossom Sword is the instructor?

Some men's expressions are bright, while others are hazy or sinister.

At a time when I was brimming with energy, the most beautiful teacher in the world? Surprisingly, there are many stories of forbidden love and presumptuous knightly destruction in Zhongyuan.

But that's that and this is this.

Wasn't Heavenly Blossom Sword known as a master of Semi-Unrestrained Realm?

She was a practical expert who has sufficiently proven her combat prowess through violent life-or-death matchs in the eastern part of Zhongyuan.

So, she was a true master, and she didn't have the words that are often said of young masters, such as, 'He's still young and inexperienced in combat, so he can't actually show his power', or 'He's weak-minded because he's not used to killing yet'.

Since she had easily defeated three Transcendent Realm masters in many fights, there was an argument about whether she could face an Unrestrained Realm master or not.

That was the reason why the strange and not even funny saying, "Jun Hwa-kyung" came out.

And she's a woman.

There are so many areas that should not be targeted, such as the face, chest, and pelvis, that it is difficult to properly perform a herbicide.

So, it's not easy for applicants who want to show off even just a little more of their strengths to step forward and say, "Let me show you something!"

Trembling gazes and anxious eyes pass busily among the examinees.

You go, no, please go, no, you go.

But if no one steps forward, everyone will be laughed at, and I don't want to step forward myself.

Even after seeing that, doesn't Qing know?

Look at these, I thought, and a feeling of slight resentment welled up in me.

Soon, a young man let out a long sigh and walked out.

"I would like to greet the Great Expert. I am Yang Qi from Zhaoqing."

"I'm Ximen Qing. Great Expert? Given my youth, this title is too much for me. Please don't exaggarate."

"Aren't you already a warrior on the verge of achieving harmony? And you're even an instructor."

"Hmm."

Qing pretended to be embarrassed. She just pretended.

\textit{Well, I am a great expert.}

\textit{If I were just a Young Expert, shouldn't everyone below Unrestrained Realm be called a Very Young Expert or a Super Young Expert?}

\textit{What does age matter in the martial arts world? It's the strong who win.}

It was actually the thought of the person who respected her elders the most.

"I, Yang Qi, dare to ask for your instruction."

"Okay. Come."

Anyway, in Qing's eyes, he is a remarkable young man.

He was a young man who took up arms during a battle of wits, so what could be so special about justice and chivalry? This is justice and chivalry.

However, compared to his uniqueness, his skills are, well, nothing.

The power within the sword can be felt, but it is not revealed externally, so it has not yet achieved sword spirit, so it is second-rate, second-rate, or later?

Oh! What a rude thought I'm having. Dividing the second-rate into beginner, intermediate, and advanced is truly an insult to the unmanned. What are you talking about dividing breathing into early, intermediate, and advanced stages?

Anyway, Yang Qi's honest swordsmanship flies in at a rather brisk speed.

After a split second of hesitation, deciding whether to block or dodge, Qing twists his body as his soles slip half a step.

To others, it was a sword strike that barely grazed an inch of the chest, but to the master of Hwagyeong, it was just an inch away, so with a little exaggeration, it would be like the distance between the sun and the moon.

Boohoo, boohoo.

The two-edged sword continues to cut through the air.

Qing gracefully and gently departed from the trajectory, which also meant that she had enough leisure to take care of elegance.

Honestly, I can't really call it skill.

Especially swordsmanship, what kind of strange things did he pick up and learn?

The movements are large, the overall shape is vague, and the continuous attacks that are cut off from each other by the blade are very awkward, but they are familiar to the eye.

The Great Wind Sword. Was it blue or white? It doesn't really make much of a difference, anyway.

Since the area below Qing border is not considered a martial art, the martial arts that were stolen and learned are already densely lined up in the martial arts window.

In an instant, the Fusshen-di stretched out forward.

Qing took a big step and gently touched Yang Qi's knee, which was floating in the air, but she pressed down with a force that was impossible to resist.

Bang, Yang Qi's soles sink.

In the middle, my body is thrown forward as my forward leg is forcibly shortened by half a step, but the swing of my upper body, which I have become accustomed to from countless swings, remains the same, and thanks to that, my center of gravity is suddenly thrown forward, and boom!

Yang Qi paused. Just now?

He could tell instinctively, by the sound and the strength in his hand, that this was the most outstanding move among the four great wind swords he had swung so far.

Yang Qi forced himself to hold onto that fleeting sensation. How was it? Was it like this?

Clang! The sound of swords and flutes clashing resonates loudly.

Qing nodded. \textit{Hmm, that's much better. Did this person learns martial arts from a book?}

The brain-scratching learning of Qing is a form of forcibly instilling the most perfect understanding from the point of creation of the martial art.

Instead of having any interpretation of her own, she was able to unfold the most ideal form that the creator had in mind. This was the thought that suddenly occurred to her as soon as he saw Yang Qi's first strike.

\textit{What was it? Leg splits? Land grabbing? Flexibility exercises? It's like crossing the ocean.}

Qing really liked Yang Qi's attitude, that he had stepped forward because no one else did.

So instead of just laughing it off and moving on, she held out her flute and pressed down on the knees that were reaching out so far away in an ignorant manner.

The knee fell to a suitable position.

Originally, there was no detail in the Martial Arts Manual.

Consider the learner's physical requirements.

There is no Manual in the world that tells you how to calculate your stride length based on your height, the proportion of your legs, and where your knees are.

Usually it just described as 'moderately', 'far' and 'narrowly'.

If there is even a picture drawn, it was already considered more detailed than normal.

Because the Manual is not the main teaching material, but merely a supplementary textbook or teaching aid.

In particular, the basic form of external training is for the master to directly teach to the disciple, and the martial Arts Manual merely assists him.

Of course, there are also Secret Manuals written by masters who were unable to take on disciples so that future generations could learn on their own.

They were very detailed and well-written manuals, with the phrases like 'the feet two inches forward, the waist bent as if facing the sun of the horse, and the arms doing this and that'.

Widely known Martial Arts Manual are often called annotated books and even have such units written down.

But the problem is the primitive and uncivilized weights and measures of our time, and the primitive and uncivilized weights and measures inevitably take the human body as their standard.

One cun (寸) is the width of an adult's thumb.

One chi (尺) is the distance between the tip of the middle finger and the tip of the thumb when an adult's hand is fully outstretched.

Because no matter how big or small a person is, they are all the same, slightly different, but not that different.

But what if that happens, when it becomes a Martial Art Manual?

Everyone's fingers, arms, legs, and even torso proportions are different, but this is especially true in the external martial art, where the body must be used most efficiently.

So, first, learn it in a rough form.

And only then can we achieve optimization through the process of gradually learning martial arts from the ancestors' to our own.

It was one of the reasons why experts come from old and prestigious families.

Many people have practiced the same martial art for a long time, so they have something that can be called a sum of materials or experiences that can be taught in the right way from the beginning.

What about the ronin or even the disciples of minor sects?

There is no such thing.

First, do as it says in the book, and then make it a habit and change it.

To begin with, the applicants for admission to the Yizheng Martial Study Hall were at that level.

That's fortunate, since half of them are third-rate warriors who only know how to swing a sword and do a few external attacks.

The Fushen-di gently cut through the air.

Pushing the ends out to the sides of the pelvis, sometimes digging under the elbows and leading them up, forward, and outward, poking the chest to make them retreat, or slapping the back to make them cringe.

Yang Qi's stance changed little by little.

The sound of the sword cutting through the wind fiercely changes into the sound of a great wind (大風) that is worthy of its name.

As the body was twisted and turned, the center of gravity was drawn to the sword, and a heavy force was concentrated on it.

In the meantime, Yang Qi gritted his teeth.

He was struggling to not fall.

Every time Qing pushed and pulled, his center of gravity twisted, and every action of recoil to correct his body was doubling his sword power.

He vaguely knew.

\textit{I don't know why, but it seems like she's taking great care of my martial arts.}

\textit{This is may be a more important opportunity now than entering the Yizheng Martial Study Hall.}

\textit{And again.}

\textit{This is a once-in-a-lifetime opportunity. If I fall now, this teaching will also end.}

In this part, Qing may feel wronged.

'No, if you fall, just get up. Why end it here?'

But that's why he was been working so hard and concentrating so hard, to the point where he had never worked so hard since he was born as he did now.

The crowd watched in silence.

A clumsy and awkward warrior gradually changed into something more plausible (because the crowd lacked the insight to read martial arts).

However, it is easier for others to see a properly powerful movement than for the person doing it.

Because the fetus comes out.

Why, even in the hometown of Qing, even if you had no knowledge of the matter, when you saw the exhilarating movement of kicking or hitting the ball, didn't you immediately think, 'Ah, that's the right technique'.

Heavenly Blossom Sword say she was the instructor, but even just as an examiner is he still teaching!?

Meanwhile, Yang Qi was drenched in sweat.

It is a black, light object, but it is by no means a light object when wielded.

If you desperately try to control your body while it's spinning, you can't just use force.

So, even with his humble Qi reserve, he can unconsciously control his Qi and add strength where needed to endure, relying on his focused mind.

This is the essence of the mental power that the unmanned person speaks of.

And at some point, Yang Qi suddenly felt the subtle pleasure of the last handful of true Qi in his dantian, that one faint ray, leaving his body.

It's a different feeling than when his lacking self losing energy through inefficient training.

From me to the world.

From the inside out.

Just as an egg becomes a chick, the feeling of infinite liberation as if breaking out of the egg and finally reaching the world.

Suddenly, a faint ray of light followed the blade, and quickly disappeared as if it had never happened.

Yang Qi's body stood still.

\textit{Just now, no way.}

"Congratulations, Young Expert Yang. You've reached the First-Class Realm."

Although he felt like someone was muttering, 'Haiya, just a First-Class" or 'A hallucination?'. Either way, it felt like he was hearing things.

But there would never be anyone like Heavenly Blossom Sword, the kind and gentle Master himself who would impart such great teachings even to a nameless ronin!

\textit{Am I hearing things because I'm tired?}

\textit{Rather than that.}

Yang Qi's eyes trembled.

\textit{Me, me, First-Class?}

In fact, Yang Qi was just lucky.

The martial arts he learned at the local martial art school after selling half of the main beam of his house was the Great Wind Sword.

Qing learned that Great Wind Sword by stealing it from the market stall, and since it had a blue border, she just thoughtlessly upgraded it to Eight Star.

From the beginning, her personality was such that if there was a situation where everyone would suffer, she would step forward and try to solve it even if it meant suffering losses herself.

This time too, it was just like usual, nothing special was done.

What if that weren't the case?

Qingdo, what the heck, oh my, what the hell is this? I came out feeling a bit shaky, and this is like, "What the heck, I'm going to teach these kids?" He would have pretended to stop them and gone back.
