\chapter{The New Semester Has Begun (1)}

The Yizheng Martial Study Academy was held in Laosan, Henan Province.

It was a slightly ominous name for Qing.

'Laosan'\footnote{'San' means 'mountain'}? Mount Lao again?'

However, Laosan was the name of the county, and there was no Mount Lao there. Instead, there was only the lofty Mount Baiyun.

It was Laosan without Mount Lao.

The reason why the school was located on the deep Chilbu ridge of Mount Baiyun in Laosan County, rather than in Kaifeng area, was simple.

Because there was a mountain there.

It's like having the same mindset as a mountaineer.

The importance of mountains to a growing unmanned species cannot be overemphasized.

The mountain itself has the effect of clearing the mind and healing the body and soul, and even if you just let it run wild, it builds muscles, strengthens bones, and creates tough skin.

On the other hand, water was abundant, food was plentiful, and it was easy to obtain materials and firewood.

Is that all?

In a private home, that is, cut off from the world, there was no room for other things, so naturally, one has no choice but to devote oneself to cultivation.

Why else would the legendary warriors in folk tales all come from the mountains?

Even in the future, in Qing's hometown, wouldn't it be said that a school would be best if it was on a mountain?

Although many schools have moved down to the mountains, educational facilities that require training, such as boarding schools, prayer centers, and training centers, were located deep in the mountains in remote, uninhabited places.

Anyway.

After a long time, the Dragon King's maiden descended, waving the Dragon King's plaque. The Dragon King was a water god with omnipotent power who was free from even taxes.

It was only regrettable that one of the lucky ones among the ship owners who were drawn to that brilliance was born, and that they spent a short time together from Jagwi to Hyeongju.

And from Hyungju, the journey was simply a matter of going straight up north.

After taking Hyungmun, take Yangyang, and pass Namyang and keep going.

So, Pingdingsan!

It's the name of a city, not a mountain.

Although it was a large city with a population of over 100,000, it was also an unfortunate city that cannot even hand out business cards in terms of population because it was in Henan.

There were many cities famous for their history and scale, such as Luoyang, Zhengzhou, Kaifeng, Xuchang, Runan, and Puyang.

Because Henan Province was the center of the era and the best granary that could feed the entire Zhongyuan, which was once narrow.

It was also the city where the first entrance exam for the Yizheng Martial Study Academy was held.

Of course, a person who was not well-off was a person, so it was impossible for them to take the test at the remote foot of Mount Baiyun.

It might be possible to feed and house the overflowing number of applicants in the mountains, but there's no reason to go that far.

So, the city of Pingdingsan was literally simmering with heat.

The warriors who gathered in search of their own dreams of prosperity.

The city's expression was as bright as the number of guests who flocked there.

If this many people gather together, there will inevitably be problems.

But with the martial arts alliance exam just around the corner, there's no way anyone would cause an accident, whether for the sake of the exam or out of fear of the martial arts alliance expert who was the examiner.

What a mess!

There was a chance!

Qing's head suddenly turns.

A young man jumps down through the sliding door on this floor. Either because his martial arts skills were poor or because he was in such a desperate situation, he falls down with a crash.

Even though it looks like he's in a lot of pain, he suddenly gets up and runs towards me, and then another young man with a sword jumps out from behind him.

"Die, you enemy of the family!"

At the words of the young man pursuing him, the warriors who were holding their weapons to stop him stopped in their tracks.

He's the enemy of the family.

For a person of Zhongyuan, family enmity was a serious matter.

If you don't pay it back, you will lose your human status and will not be treated as a human being.

"No, shit! Why me, not me, ugh!"

The young man being chased by his enemy suddenly rolls on the floor.

Someone extended the scabbard.

The young enemy, who was running vigorously, was caught in the neck, so his lower body was blown away.

"Ugh, ugh."

The young man rolls on the floor, his breathing heavy.

"Thank you for your help!"

After that, with a shout, the pursuer youth took the ball with one hand and headed towards Chuck.

And then, with bulging tendons bulging out from the hand holding the sword, he strides towards the young enemy who was rolling on the floor with a distorted expression.

The look in his eyes was so fierce and life-threatening that anyone who saw him would know that he was going to end things right away.

"Eek, wait, let's talk! Let's talk."

The young enemy boy crawls back while sitting and shouts in a trembling voice.

Then, suddenly, something pushed my back hard, and I was left struggling, just sweeping the floor.

That's because behind him, a woman carrying a child stretched out her leg and stopped the young man with the sole of her foot.

Until a few years ago, a cotton veil was a unique item that attracted all eyes.

However, in recent times, it has become a common outfit to see as cotton veils continues to be popular.

Of course, this time I was the one who started the trend.

Meanwhile, the pursuer, a young man, closes the distance between them, and Qing speaks in a stern voice.

"Stop."

It was a group of veiled women.

A large woman, a rather large woman, a standing child, and a child in her arms—there were four people wearing veils at the same time.

Above all, the tall woman who was pushing the man's back with her chin was unusually armed.

On his back was a huge sword that even a man would struggle to swing.

On his waist were two swords, a long and a short one. No, looking closely, the short one was a dagger with unusual decorations, and the other was a dark, ugly-looking iron flute.

"I may not know who the Young Lady is, but my name is Shao Yindiao. He is the enemy of my family—"

"Stop. If you're going to kill someone in front of a kid, then I have to stop you, right?"

Qing blurted out.

Two people flinched at her.

One was the young tracker Su Yindiao, and the other was Ciyu.

Ciyu, who had been observing this situation with interest, her dull eyes sparkling for a change, couldn't help but be startled by Qing's words.

"Then, I will take him away."

"Hmm."

Qing looked at the two young men.

Originally, there was no reason to stop someone who wanted to avenge his family's enemy.

I made excuses, but honestly, I wonder what the big deal was about the child seeing more blood now.

Unlike my hometown, the primitive ancient Zhongyuan were extremely dangerous and dangerous. I don't know if Zhongyuan customs were like this in my hometown, but I'm not sure if seeing blood in the martial arts world was something that should be avoided emotionally.

However, the unusual gaze of Qing, who was working for the first time in a long time, and the Western numbers engraved on the heads of the two young men were concerning.

I don't know the exact calculation method, but objectively speaking, evil and good karma were roughly equivalent.

However, there was some controversy as to whether past evil deeds can be replaced by good deeds, or conversely, whether it was okay for a good person to commit some evil deeds.

Still, I could figure out how that person had lived in general, unless he was some strange perverted serial killer who killed people and saved others in return.

The tracker's evil deeds amounted to just over ten points. This suggests he lived a fairly harmless life in Zhongyuan.

The young man being chased has thirteen points for his good deeds.

"I already understand why Young Expert wants to avenge his family's grudge. But what about this person? He clearly said it wasn't him."

"That's a lie. He's Wen Feihou, the eldest son of Wen Family Restaurant\footnote{Ciubang meant more of a place of making and serving alcohol} bastards. Anyone in Eomchang will testify about Wen Family Restaurant's atrocities."

"What? Eomchang?"

Did I hear that correctly?

No, was there this kind of culture in Zhongyuan too?

"Yes, this was Eom Chang-hyeon from Jiangxi Province."

"Ah, Eom Chang-hyun."

It seemed to be the name of a neighborhood.

Come to think of it, wasn't the name of Gangseo-seong, the name of the central city, Namchang?

Isn't there something wrong with that neighborhood?

But there were more than one or two cities in Zhongyuan that have ~chang.

Rather, it was a whole kitchen.

The group that was usually called a room at the back was usually made up of people who work both as office workers and unemployed people.

And usually they were a bit evil.

The selfishness of the merchants, and the cruelty of the warriors.

This was because most people only take the bad parts of these two professions.

Haven't you experienced it countless times in the land of Yangguang, including Qingdao, Guangdong, and Guangxi?

"Hmm. That's what he said. How about you?"

"It's true I'm the eldest son of the Wen Family, and it's also true that I'm one of the Sapha bastards that Ongaju family would beat to death. But I feel wronged, really. I ran away because I didn't want to live like a Sapha bastard in that damned house, so why should I be the one bearing the brunt of that resentment…"

Then, a chorus of jeers erupts, saying, 'Oooh, trash'.

Of course, the ruling ideology of Zhongyuan was filial piety.

Even if his family was a shameful and evil group of human scum, it was something that his son, or even his eldest son, should not say.

In fact, this was a powerful weapon of the East, and there was a representative example called Kim Satgat among the Korean people, the spiritual roots of Qing Dynasty.

You cursed the traitor, but he was actually your father?

No matter how evil a piece of trash he is, if a child curses his father, he doesn't deserve to be human.

So, he was a sinner who could not see the sky, so he wore a hat, and he was a sinner who could not live on the ground, so he wandered around his whole life.

But Qing doesn't understand.

If you ran away because you hated your home, isn't that the end?

And looking at the good deeds, I see that I lived well.

"Hmm. That's true. Honestly, was it right to lump them together and treat them as enemies just because they were born into that family?"

"Originally, Wen Family Restaurant was nothing more than a small brewery. But they murdered my grandfather and stole his business, achieving great success. And my family was shattered. My father, until the day he died, coughed up blood and cursed those damned bastards, never closing his eyes."

Xiao Yindiao continued speaking, glaring at Wen Feihou with cold eyes.

"Everything that he has grown up in luxury with came from my family."

"Well, at least for he cut off his family ties."

The system of collective punishment was a system where children inherit the sins of their parents.

It was the most powerful means of governing humanity, used effectively regardless of East or West, and had a very powerful crime-deterring effect, preventing people from daring to commit crimes by taking their children as hostages.

However, that wasn't right.

It was just as Qing was making up her mind.

"Even if that guy suffered greatly from childhood, he was saved by an expensive and precious medicine. Can you really say that someone who survived by drinking the blood and tears of our family was innocent?"

"Hmm, it's suddenly getting ambiguous."

Qing put his hand inside the cotton swab and scratched the back of his neck.

If you don't want to pass on sin, you should naturally not pass on property either.

It's so unfair and fatal to pass on the good things and not pass on the bad things.

If a child of a conman earns money by defrauding others, receives a good education, was given many opportunities, and becomes very successful, was that child truly innocent?

A family that has been defrauded was completely ruined, and a family that has already been ruined will continue to be ruined, so aren't the children of the victims completely deprived of the opportunities and benefits that they should have had?

"But, I feel wronged. What on earth did I do wrong? If I had known, I would have refused treatment. I was still young at the time, and I didn't know that my family was so vicious…"

Qing looked at Wen Feihou's Righteous Karma with complicated eyes.

\textit{I wish he could at least be shameless.}

Wen Feihou's speech was weak and his voice was weak, so you can tell what kind of person he was just by looking at him.

This was the image of a spineless, generous person who cannot stand to see someone in trouble and cannot refuse a request from someone else.

Qing lets out a deep sigh.

Actually, she had already made up her decision.