\chapter{The New Semester Has Begun (12)}

Since ancient times, the punishment for a fool has been a slap on the back. Of course, this was a time-honored principle without any basis or reason.

However, the nature of those who were hit on the back was similar regardless of East or West, past, present, or future.

Qing, who had burned a large handprint on his back with white phosphorus, spoke with a disgustingly elegant and gentle demeanor.

"The martial arts of the Sohyeop were powerful, but they seem to be trying to gather the energy of nature first. I simply attacked and blocked them before they could do so."

"But, isn't this a spar? How can you do this before I've even demonstrated my true abilities?"

It seems like Cai Shengxia was very wronged.

Of course, it would be embarrassing and unfair to run around the unarmed area three and a half times, trying to rub his back which was out of reach.

"What do you do when you see a boulder rolling down the hill? Do you just sit there and wait until it's within arm's reach?"

"What are you talking about-"

"Or not."

Qing's voice interrupted Cai Shengxia's words.

Qing had a beautiful voice, and possessed both precise pronunciation and beauty that attract people's attention.

"Shouldn't you try to avoid it by pulling away in advance, or digging a hole for the rock to fall into, or pushing or breaking it before it can really gain speed? That's simply what this instructor did."

It had already attracted enough attention.

Qing brought up the main point.

"Master White Tusk Sword, who tested Young Expert Cai, simply observed you sufficiently to judge your skill as an examiner. If it had been a real fight, Young Expert would have been losing your head before you could even make your first move."

'Don't be overconfident that you beat the examiner, and don't think that you really won.'

Qing knew that the martial arts that deal with the natural Qi were different from the martial arts of Zhongyuan.

Well, that's because she was a true master of Unrestrained Realm.

The martial arts of Zhongyuan, which were based on the great ideal of self-cultivation and self-perfection brought from India to Zhongyuan, were a fierce cultivation of 'one's own', taking the energy of nature and coverts it to Inner Qi.

But Cai Shengxia's Azure Dragon Dance was different.

Even if you rated your own skills highly, were they truly first-class skills?

His humble Inner Qi was simply used to gather and guide the nature Qi, so it must've bee a martial art with a different fundamental root.

If it doesn't have deep roots, it could have been created from scratch by one of the eccentric people of Zhongyuan.

Nature Qi were infinite, so it might sounded impressive to say he wielded them.

But why bother?

Martial arts was ultimately a process of expanding from one self to the world.

Therefore, if you fill yourself with the Qi of the world, you were in a Second-rate Realm. If you made the weapon you have in your hand into an extension of yourself and fill it with Qi, you were in a First-rate Realm.

Peak Realm is the state when that Qi reached out into the world.

And the moment when two objects first meet was called a collision.

The universe begins with a collision, and a chick must hatch from an egg to meet the world, so the first relationship was a collision, a fight, and destruction.

Therefore, at the moment when the inner self of a person begins to connect with the world, it attempts the most violent conversation, like starlight, to shatter and burn the darkness of the universe.

The state of transcendence, Transcendent Realm.

Previously, Qing technically was not a martial artist at all. After all, what martial artist in the world would learn martial arts by seeing and manipulating illusions floating in the air and receiving brainwaves?

But now, despite the accumulated good karma, Qing didn't really try to find new Divine Arts through Good Karma Exchange.

Because martial study was a journeys, a path that leads to the same destination, although the paths were different.

That was why it was said that martial study was like the path of water that eventually reaches the sea.

So, even if you had to learn a new skill, it was just a reference point that guides you to the end.

So, the new skill was just a tool for survival.

The more you have, the more you can defeat your enemies, right?

If there were too many different types of training, it becomes difficult to choose and you end up losing your way.

Increasing its mastery doesn't guarantee that you will immediately reach the current state or a higher level.

Until the Peak Realm, it's like she was so hungry that she swallowed the raw food without even chewing it.

But since then, Qing had reached higher realm on her own. She's no longer a weirdo who just memorized names because they sounded cool and couldn't tell the difference between Demonic and Divine Arts, completely ignorant of Wulin.

Rather, she was now a true master of Wulin, a senior in Jianghu who had enlightened countless groups through countless new techniques, and a martial artist with profound Inner Qi.

And this body, in the eyes of a true master, a great senior, is… um, Azure Dragon Dance? Nature's Qi? Well, it sounds impressive.

Nature exists even at the end of the martial arts of Zhongyuan.

There were only a few recorded instances of reaching it, but anyway.

The sword called 'I' that one self have trained and forged so terribly and rigorously, one will finally let go of it all and enter a state of non-action, where 'I am nature and nature is me', where there was no self and the world was self.

If you wield the wisdom of nature first?

So to speak, you skipped the middle and just use a little bit of sea water.

Of course, the pursuit of a completely different martial arts discipline, whether it be Azure Dragon Dance or Azure Dragon Twirl\footnote{In the original text, it's 'dance' with different Hanzi character, 춤}, may be different from that of the martial arts discipline of Zhongyuan, right?

\textit{I'm curious about that, but I don't think it's surprising enough to be called that great.}

There were always voluntary commentators who showed up whenever a fight breaks out in Zhongyuan, whether it's a martial or non-combat type fight.

Why did those always appear?

Are there any educational institutions that teach this kind of commentary?

Of course not.

This was because the ability to see the situation, the battlefield, and the situation was not a professional occupation, but rather a field of culture.

When more outstanding commentators were present on the battlefield, those who lack confidence in their skills and insight quietly shut their mouths and return to being onlookers, listening to their commentary and developing their own insight.

But what if there was no one with any discernment?

'Then why don't I do it? This is my chance to show off my insight by adding commentary?' That's why those incompetent people came forward.

In other words, those who open their mouths without receiving montary compensation for their commentary skills (we don't know what the concept of commentary skills is, but anyway) lived off of attention.

And they didn't miss this opportunity.

"Heavenly Blossom Sword's words make sense. The examiners aren't sparring or fighting. They're simply there to help you unleash your full potential. So, it's a bit difficult to say that Young Azure Dragon defeated White Tusk Sword."

"Well, real combat is a different story. There were warriors who were exceptionally strong in non-combat weapons. And if that's the case, what about the Sichuan Tang Family, renowned for their extreme poison and hidden weapons? Is there anyone in Zhongyuan who dares to disrespect Tang Family's reputation?"

"Young Azure Dragon's martial arts are incredible and of course amazing, but it takes about five breaths to actually unleash its powerful attack. A master skilled in the art of flash step would be able to unleash a killing blow with more than enough time."

"White Tusk Sword is the leader of the Chi-ui-dan, the combat unit of the Wulin Alliance, and a disciple of Great Jeom-chang. Jeom-chang's swords are incredibly powerful, and White Tusk Sword is also renowned for his ability to pierce his enemies with a single, devastating blow, like a wolf biting a man's throat. White Tusk Sword was helding back his own strengths and gone on the defensive, so as Heavenly Blossom Sword said, to call him defeated would be unfair."

However, it was somehow biased.

But it's always been like this.

Because what the experts say was the truth.

If you try to express an opinion that differs from that of an expert, you will only be scolded for speaking out against your own abilities, and you will not even be able to refute it.

When Young Azure Dragon defeat White Tusk Sword?

Along with the excitement of witnessing the birth of a new master, they sided with the master based on the simple and clear rule that the winner was the master.

But what happens after Heavenly Blossom Sword hits Young Azure Dragon's back hard?

Heavenly Blossom Sword was much more skilled!

But there wasn't some grand movement.

She simply ran up and struck the back with a terrifying blow that sent chills down the spine of those watching. In any case, even to the crowd, it did not look like some noble or flashy attack.

Cai Shengxia was embarrassed.

The reason he came to Jianghu was to carry on his master's will, and it was for his sake.

It was the fate passed down from generation to generation for the successors of the Four Directions Dance to subdue the masters of the Red Fenguhuang, White Tiger, and Black Tortoise, obtain their martial arts, and perfect the Four Guardian Gods Dance.

If he make a great name for himself in Jianghu, the masters of the Four Guardian Gods Dances would come looking for him.

Or, there may be some among them who wish to enter Yizheng Martial Study Hall.

And for personal reasons.

'You're saying that learning martial arts can seduce women? You punk, haven't you ever heard the saying, 'A hero has three wives and four concubines?' Women were bound to cling to a master. Just show them a little bit of martial arts and they'll be hooked. So, will you come with me?'

That was the reason why an eight-year-old boy was stuck in the mountains for over ten years, dancing all the time.

And as if by some fate, he met the most beautiful woman in the world (according to about eight out of ten people).

Women unconditionally adored strong men. This strength meant not only physical strength, but also boldness and confidence, unhesitating in speech and action, and ambitions as vast as a mountain.

He used the temptation he learned from his master!

With bold, confident, and unhesitating words and actions!

'What? What if a woman is strong in martial arts? You punk, the Azure Dragon Dance you learned is the best martial art in the world, and if you succeed, you will have no rivals in Jianghu. Besides, there were no women as easy as female martial artists. If you say, 'Let's fight one-to-one', they have a lot of pride, so they'll rush in right away. If you turn the table and subdue them, that's the end. From then on, they'll just cling to you, saying they'll die if they're not by your side, right?'

However, why did Cai Shengxia, now that his master was old, wander the world alone, looking for a qualified disciple?

Why was it that among the countless women who were said to be unable to live alone, not a single one came to the mountains to visit?

In the end, Cai Shengxia took charge of everything, but why was he really good at cooking, cleaning, and doing laundry when he was still a child?

Cai Shengxia should have questioned this part first.

Cai Shengxia was too young at that time.

Unfortunately, only the two of them lived together until they grew up, so there was no reason to question it after that.

Cai Shengxia clenched his fist.

\textit{The years I spent learning martial arts while living with my master, without even seeing a man, let alone a woman, and learning martial arts while taking on all the housework and getting beaten, the pain I had to endure during those long years… …!}

"As Young Lady said, I let my guard down, but I will show you properly this time."

It was a little ugly to make excuses, but still.

There were a few problems with the process.

It was also true that he let his guard down.

-Hey, you should ride the wind properly. Why are you drawing the wind towards you? What, is this cool? Hmm, that's true, but…

Heavenly Blossom Sword.

She was the most famous young master and female martial artist, considered to be the next Greatest Under Heaven, or at least the Zenith Among Women, and was certain to become the next Sword King.

If he defeated her here, his name will spread far and wide, and revealing the true martial arts to Zhongyuan and fulfill his clan's long-cherished wish.

Furthermore, he would take the most beautiful woman in the world, captivated by this incredible and true martial arts, as his wife.

"Hmm. Right. Properly."

Qing thought for a moment.

Actually, it'd be fine if she didn't accept.

But she's curious.

\textit{The process of attracting the natural energy through dancing is full of loopholes, so I wonder if it's a serious disqualification as a martial art.}

\textit{Actually, there are more than one or two ways to counter it, even if it's not on the back. What if I just use the Tathagata Divine Palm from a far or throw a battle hairpin?}

\textit{With one hit, you'll stode before King Yama.}

\textit{If not, was there another way?}

\textit{But if there was a way, why didn't you use it sooner?}

\textit{Surely he wasn't just trying to show off because his dancing was cool. Of course, it was cool in it own way, I did imagine myself performing some kind of Qing Dragon Dance or something.}

"Then, I'll give you the first move."

"You still don't take up your sword?"

"That depends on how well you do, right?"

Qing tapped the buckle on her waist, as if saying she could pull it out at any time, but it was up to him whether he would pull it out or not.

Then, she took the martial arts stance again and put her fingers together and wiggled them.

At that, Cai Shengxia's expression changes completely.

Beyond good and evil, like and against, just like a beast of prey, a certain intangible energy that sinks and rises.

Soon, Cai Shengxia takes his foot off the ground.

Not forward, but sideways.

Qing's eyebrows twitched. 

\textit{Could it be? He got hit while coming forward, so he's going to dance to the side to gather his energy? If that's true, I should have just refuse it. He should have just gone home, applied some ointment, and waited.}

Then, suddenly, a sense of discomfort washed over her.

Qing not only saw the world with her eyes, but also with her skin.

Divine Thief's Awakened Sense was sensitive to the flow of the air, and by accumulating those experiences, she learned how to detects movements within a certain radius.

And now, Cai Shengxia's movements were completely absorbed into the flow of the air, like an illusion that existed without form, completely unperceived by the senses, and felt like an empty space.

To go with the flow, you must first read.

\textit{Well, this guy can use something similar.}

\textit{If you can still see and feel the enemy even when you turn around, then it's okay to just turn around and show your back.}

\textit{I guess it wasn't a lie when he said he let your guard down?}

Qing carefully observed Cai Shengxia's toes.

Since the center of gravity was placed back, it looks like it can quickly picked up speed and ran out in any direction.

Even if you launch a surprise attack now, it won't work.

It had a more serious appearance, and the dance line was narrower and slower, so it looks a bit broken and has a sloppy gesture to it.

Sure, it was cool before. Not so much now.

But with each step, the energy was clearly felt.

Rather, the movement was reduced and the speed was slow, but with the sound of the sharp wind whistling, the blades of wind that were visualized in the eyes surged and gathered-

"Here I go!"

Cai Shengxia shouted and ran towards them.

\textit{This kid. He's using informal tone when he says he's going.}

A blade of wind swirling everywhere.

And Cai Shengxia's sword takes the shape of a huge blade, and a huge blade that was almost five feet long was parallel to the ground and rushes towards Qing.

Suddenly, Qing's figure disappears without a trace.

It's a trivial action.

Lower your body until your knees almost touched the ground, your hips were level with your knees, and your torso bent backward.

The moment the blade passed over her head, Qing's right arm rose upward.

Long, slender fingers gently stretch out and lightly grasp Cai Shengxia's wrist, pulling it with a weight that was by no means light, like a thousand pounds.

Qing suddenly got up and stood as if nothing had happened.

Her left hand was clenched into a fist and held close to her side, ready to be fired at any moment like an arrow placed on a bow.

The indestructible, evil, White Hand Witch's nuclear fist dug deep into Cai Shengxia's solar plexus.
