\chapter{The New Semester Has Begun (5)}

Nan-Gong Shencai's priority was swordsmanship, so he had a very indifferent reaction to Chiyu.

"Oh, so you're a Sword Niece\footnote{劍姪; Jianzhi}. Hello?"

What is even Sword Niece?

Well, there are fraternal relationship in the Orthodox Sects and Noble Families, and a friend's daughter could be considered a niece, so a daughter of a Sword Friend becomes a Sword Niece.

"By the way, Sword Niece's wooden sword is truly magnificent. It looks just like the wooden sword of the family. Oh, did my father give it to you as a gift?"

\textit{It seems like he doesn't call his father 'Sword Father'.}

\textit{What, there's no Sword Father, Sword Mother, Sword Older Brother, Sword Younger Brother, Sword Child, Sword Sister? Sword Older Brother and Sword Younger Brother sounds pretty cool.}

\textit{The rules seems arbitrary.}

\textit{Well, I guess there's no such thing as rules for a lunatic.}

"Yes, Sword Niece. Have you ever heard of this story? The sword is the Gentleman of Weapons. The word '君' means supreme, the most noble. And of all the things humans do with tools, swordsmanship is the most beautiful."

"Really?"

"Of course."

"Really?"

Ciyu looked at Qing as if to ask if this was right.

Qing was momentarily conflicted.

This was because among the people Qing knew, there was no one who taught swordsmanship as well as Nan-Gong Shencai.

It seems that the pinnacle of swordsmanship, the humble and shameful state of things, was due to the fact that a large portion of it was devoted to the ability to teach others.

For a young man who pursues self-study, there is no way to make him enjoy swordsmanship, that is, the act of swinging a sword and tiring both body and mind.

So, I was wondering if it wouldn't be a good idea to ask Nan-Gong Shencai to teach me some introductory lessons on swordsmanship.

But Ciyu is only slightly affected by that.

"It may be different for everyone, but that's how it is for Sword Uncle."

"Sword Uncle! Yes, I'm Sword Uncle! So, does Sword Niece like drawing? Drawing with swords is really fun, but I don't know how to explain it."

"Drawing?"

"Well, it's twice as fun if you draw with someone. Is there anyone who would like to do it with me?"

Chiyu looked at Qing again.

This time, it was a look of asking for permission.

When Qing nodded in agreement, the two of them went out into the yard and started swinging their swords around.

It's not swordsmanship or anything yet, but from a child's perspective, it's meaningful that she's playing around with a heavy ironwood sword (small).

Aren't you surprisingly good at handling children?

I don't know if Nan-Gong Shencai was originally like that, or if it was some desperate sense of mission to somehow lead my swordsmanship to the path of the sword.

According to the Analects, if three people walk together, there will definitely be a teacher among them. Perhaps this is the attitude of a teacher worth learning from.

Do you like drawing, everyone? Today, we're going to draw with a sword.

Does it sound plausible?

However, Qing is not a juvenile instructor.

It is a bit problematic that the target is already a grown man.

It wasn't a matter of age, but rather, unlike the boys' department, they were passionate students who were already ready to learn and who had come to the Department of Political Science and Education on their own initiative to find the opportunity.

Come to think of it, I don't think it needs any particular excitement, but can't we roll it out a bit?

A few days later.

A wide open space in front of the examination center building of the Department of Political Science and Technology.

Crowds flocked in from early morning and took their seats, perhaps because the primitive and uncivilized entertainment culture of the ancient Zhongyuan absolutely could not miss such a grand event.

Of course, half of them.

They couldn't hide their nervous expressions; they were the applicants for the entrance exam to the Department of Political Science and Technology.

Street vendors, who had been unintentionally hit by the storm, happily sell breakfast with their backs to the noodles, and only after the morning has passed leisurely does the doors to the testing center open wide.

I guess it's finally starting.

The crowd is buzzing, rubbing their sore necks as they wait with bated breath, their anticipation building to the max.

And then a group of drones appear in a line at the testing center building.

Some move to the wooden observation platforms built along the test center wall, while others control the crowds to ensure ample space.

A large empty space was created in the middle, and the crowd, which had become denser, was crowded together, but they didn't leave.

Soon, a man walks out.

In today's spectator culture, the more you pretend to know, the more knowledgeable you are.

Therefore, even before he could introduce himself, rumors spread among the crowd that he was Yu Shan-ye the Sword-dominating Dagger\footnote{短劍劒君; Duanjian Jianjun}, that he was one of the leader of the Wulin Alliance and that he was nicknamed Sword-dominating Dagger because he had a gentlemanly personality and would not harm his enemies but would break their weapons.

Oh, so that's why you were the Sword-dominating Dagger.

Qing overheard such sounds with her superhuman hearing from the observation deck and learned the origin of the nickname.

The 君 character was not in the sense of a ruler, but a gentleman.

Anyway, they are both the same letters.

"Dear fellow martial artists, I am Yu Shan-ye, the headmaster of the Yizheng Martial Study Hall."

Qing counted in her head. One, two.

"Sword-dominating Dagger!" "Sword-dominating Dagger!" "Sword-dominating Dagger!"

The educated modern people of Zhongyuan responded to him in an orderly manner.

Since the impatient intellectuals had already whispered his identity, they all spoke with a loud voice brimming with confidence and conviction.

Then, Yu Shan-ye continued speaking.

"I sincerely wish I could open the doors of the academy wide and embrace all the spirited young people, but I am truly sorry that the circumstances do not allow for this."

Then Yu Shan-ye continued speaking.

"What we seek in this examination is not individual inaction. The Yizheng Martial Study Hall seeks to assist those who bravely walk the lonely path even in difficult circumstances. It seeks to cultivate heroes that benefit the world, rather than those of mere experts."

Yu Shan-ye continued speaking.

"So, before the exam, I, the headmaster, would like to speak to you, the examinees, and the crowd watching. What is a chivalrous person? What is a chivalrous person?"

Yu Shan-ye continued speaking again.

"This is something that cannot be defined in a single word. If you were to ask what exactly chivalry is, not many would be able to give a straight answer, and everyone would give a different answer. That's because chivalry is such a difficult question. However, chivalry already exists in everyone's heart. This is because everyone knows what is right and what is wrong."

Yu Shan-ye continued speaking again.

"The right path is difficult, burdensome, and rarely profitable. The wrong path is easy, convenient, and offers great benefits. That's why many choose the wrong path for personal gain. However, choosing the right path despite all this is what I call chivalry. This is in the heart..."

Yu Shan-ye's words continued endlessly.

Well, it's fortunate that Qing is sitting in the stands. I didn't see it that way, Director.

I was starting to think that maybe this was the first test.

To endure endless nagging and not leave in silence.

So it tests your patience and steely resolve.

Um, but over there, red bean porridge... um, how does it taste? Red bean porridge, I want to eat red bean porridge. It's a bit disappointing that there's not much sugar in Jungwon, but it still has that hometown flavor that makes me miss it. Well, it's just red beans boiled, so what's the difference?

"……So, this is the spirit of chivalry and collaboration, so I hope that the officials of the academy, and those who will unfortunately have to part ways because they failed the exam, will engrave it in their hearts and work hard."

Oh, I guess it's over.

Life returns to Qing's eyes, and to the eyes of everyone present.

That was the moment.

"And next is righteousness!"

The life drains from Qing's eyes.

Oh, you agreed to something in the consultation.

The life drains from people's eyes.

"We often say we are righteous, we are upright, but we probably haven't thought deeply about what true righteousness is. That is…"

I wonder what's in that carrier.

Mala-tang? Beef soup? Judging by the steam rising from it, it's definitely soup. Maybe it's naejang-tang.

It was when the street vendors, unable to overcome boredom, were gulping their saliva while imagining the snacks they were carrying on their backs.

-Wow!!

Suddenly, a loud cheer filled the hall.

Finally, the announcement was made that the exams had begun.

The shouts of those who were freed from the long and arduous admonition were filled with great joy: "Finally!"

And the cheers grew louder when they saw Nan-Gong Shencai, the new man who had taken over the position after Yu Shan-ye.

Even if it's the first test, it's nothing special.

Just spar with the test tube and you're done.

In the audience, if there is anyone worth noting, just write down your opinion and submit it.

In fact, the result of the document screening has already been decided to some extent.

The judges sitting in the audience seats are, so to speak, qualified to write down a special pass, meaning that the person should be admitted, and a special fail, meaning that the person should not be admitted.

"My name is Nan-Gong Shencai, I am a swordsman!"

"Young Sword King!" "Duke Nan-Gong!" "Swordchi!"

"Come on, don't worry about it! As a student who will also be training at the Yizheng Martial Study Hall, I simply want to get a firsthand look at the swordsmanship of my fellow students!"

The eyes of the examinees sparklde.

There were already rumors going around that the young masters of the Orthodox Wulin would be joining the Yizheng Martial Study Hall as group leaders.

But the Young Sword King?

A chance to train with the Grand Duke of Nan-Gong Family! A chance to become close friends! A chance to become acquainted!

Maybe we could become friends, or maybe even just get a face painting. The importance of connections in Zhongyuan cannot be overemphasized.

Besides, is the Young Sword King the only leader?

Surely there must be many such promoters!

This is truly a once in a lifetime opportunity!

We must stick together!

It was a moment that further motivated the applicants.

The reason Nan-Gong Shencai was chosen as the first test subject was also because it was a target of the Wulin Alliance.

"Now, who wants to join me in a swordfight? Oh, of course, I only accept swordsman. No other weapons are allowed!"

With a truly sword-like sound, a young man rushes out and stands in front of Nan-Gong Shencai.

"Oh, the first poem! You are so full of enthusiasm! Good!"

"No, that's, uh…"

Contrary to his exuberant outburst, the young man's attitude was a bit hesitant.

He was in a state of not knowing where to look, as if the crowd's gaze was burdensome and awkward.

Qing was watching from above, so she could understand why the young man was acting that way.

Because it didn't stick out, it was pushed out.

The man behind the young man pushed him away, and he did so with all his might, using both hands.

What is it, eliminating competitors? Containing them?

I thought that kind of person shouldn't be admitted to the Department of Political Science and I should write down that I should remember his face and reject him, so I looked at his face.

"Youngest Brother! Show your resolve! Loudly!" "Youngest Brother! You can do it!"

It was the sound of the man who pushed the young man away and the men around him clenching their fists and shouting in support.

Oh, it wasn't about eliminating competitors, it was about being together.

It looks like he was pushed from the back to be the first to come forward.

But why, um, what is it? Among them, there's someone who looks a little familiar?

"I am! Mataja, from Yukryang! Oh, that! I'm the youngest of the Qingha Yukhyeop! I don't have much experience in the martial arts world yet! But I aspire to become a great swordsman, following in the footsteps of my older brothers!"

"You can do it!" "You're handsome! Our youngest!"

Qingha Meat Association? While Qing tilts his head, several storytellers pretend to know the crowd.

They are sworn brothers, with the eldest brother being the swordsman known as Qingha Sahyeop, Qingha Jilpunghyeop, and Jogaksan. They are a group of righteous warriors who roam the martial arts world, executing wanted criminals. Their martial arts skills aren't particularly outstanding, and they often end up on the run after defeat. Nevertheless, their unwavering determination to punish evildoers is enough to earn them the title of chivalrous warrior.

Qingha Four Brothers? Qingha Six Brothers, right? Well, it seems like they've gotten two brothers. Still, six isn't a lot, isn't it? They're all active warriors, so wouldn't it be good if they could increase their numbers? They're sworn brothers, so they could increase their numbers, right? And so on, and so forth.

"Please do me a favor!"

"Good! Come!"

And in the meantime, the real sparring begins.