\chapter{The New Semester Has Begun (6)}

Mataza's charge was like that of a protagonist in an old tale running towards his nemesis.

It seems like our fight starts now!

However, the stance with the sword was awkward and full of vulnerabilities, so I would say that it was just good momentum.

Of course, if it seemed like victory was only possible through momentum, there would be no reason in this world to practice martial arts so diligently.

If you just hypnotize yourself and use suggestions to become a strong man or strong woman, you will win.

The swords clashed, making a strangely cute sound.

That's why Nan-Gong Shencai is so lenient.

It meant that he was not harshly rejecting and striking the incoming sword strike, but rather gently accepting it.

It was a very impressive scene for Qing.

Because this is the scene that makes you realize that things are going to get quite boring from now on.

Qing looked at the blank white paper on the desk set up on the observation deck and felt embarrassed.

Hmm. Mataza. Nothing special to note.

No, in the first place, what's there to evaluate about these pseudo-unmanned beings who can't even use swords properly?

Wouldn't that be like bringing in authorities to look at a kindergartener's picture diary and evaluate its artistry?

Suddenly, these stories? Like comics.

I was curious to see how bored and unmotivated the students who came to observe the entrance exam, wondering if they were truly the best at what they were doing.

But what can I do when it's work?

People who come out to see something for fun can just leave if it's not fun, but if it becomes a job, then you have to be sincere no matter what, right?

If I had come out to see the sights, I would have lost interest a long time ago and seriously considered what to eat for lunch today.

Since I'm here today as an examiner, I still have to see it...

Then, a loud clash of swords rang out, and before he knew it, Mataza's head was caught between Nan-Gong Shencai's crossed swords.

Mataza swallows hard and says.

"I lost."

"Ma So-hyeop also had outstanding sword skills."

Nan-Gong Shencai answered with a lottery ticket.

The sound of the crowd cheering.

"Huh, Heavenly Blossom Sword? What do you think?"

Sima Chunfeng, who was sitting next to me, spoke to me.

Qing turns his head, and no matter how much he looks, it's amazing. Is this gravity? Or is it the attraction generated by a large mass? Hmm, this seems much more interesting than the first test.

In Qing's view, Nan-Gong Shencai hadn't made a single proper attack, so it seemed like he was just defending himself and taking all the hits.

After letting all the herbivores unfold like that, after going around once and seeing everything, I just took them down in one move.

"How did you feel about Samarang?"

"Kuhaha, I saw it a little differently?"

What the heck? Could it be that I see in three dimensions?

I also see it in three dimensions?

So, are you seeing it as a four-dimensional thing by yourself?

"Geniuses like us always see things others can't. For example, that Mataja, he can't quite grasp the basics of swordsmanship, but his swordsmanship is constantly changing, so he must have only been learning swordsmanship for a short time. But even so, his swordsmanship has a sharp edge, which is quite interesting. He gives flesh and takes bone. Even in his clumsiness, his experience shines through. Could he truly be considered a swordsman with a determined spirit?"

Wow, you were watching very intently.

Qing looked at Sima Chunfeng again.

From the beginning, he seemed to be extraordinary, and although he was a very strange person, he was still someone who did his best in the tasks assigned to him?

"By the way, how did you see the Cheonhwa Sword?"

"uh?"

Qing was shocked by that.

What would Qing feel?

It's just so damn low-level. I understand the level of people I have to teach. It's so petty that I want to die. Something like that?

"Huh? Hmm. Actually, even if they're on the same level, wouldn't this be a fight where the Sword Riend had the advantage?"

"Oh. Are you talking about depth?"

"No, Young Expert Ma has one sword, and Sword Friend has two, right? Still, isn't two swords better than one? So, given their current state, you could say Geom-woo is petty?"

"No, what is that shallow analysis?"

Sima Chunfeng frowned sharply, then thought, 'No, that's not true. A person as powerful as the Thousand Flower Sword. Even if she can't reach my level, a genius on par with her might have a different perspective. She shouldn't be measured by the standards of ordinary people.'

"Indeed. Young Sword King wield multiple swords. However, if that's the case, then twin swordsmanship, or rather, the martial arts of twin swordsmanship, should have been the mainstream. No, that's not true. It's difficult to reach a state with just one sword, so how much more difficult is with two? Indeed. Because of the shortcomings of those ordinary people, geniuses like you and me have gathered one or two in this era. Every day is a miracle. Yes, that's how it was. Yes, I, Samarang, sometimes overestimate the abilities of ordinary people."

I don't know what you knew though.

I know it's fun to tease people secretly.

Then, Qing wrote a review on the evaluation sheet.

\begin{quote}
	Narrow field of vision and lack of natural strength.

However, the angle of the toes is pointed towards the opponent, and the ankles are flexible, so they are good at advancing and retreating.

Have a basic sense of measuring distance.

In any case, he was a very hard worker.
\end{quote}

\textit{If you write down your weaknesses first and then your strengths, your strengths will stand out more.}

\textit{Anyway, everyone lacked skills. Isn't that why they applied in the first place?}

\textit{These are people who want to make an effort.}

\textit{I can't laugh at them just because their current skills are so poor and insignificant, and besides the great Heavenly Blossom Sword, who is good from the beginning?}

\textit{Of course they're a mess, so it's only right to write down the good points.}

"Now, wait a minute. Heavenly Blossom Sword?"

"Huh? What?"

"This, this writing, what on earth is it? The neat yet powerful handwriting, the magnificent spirit filled and without any gaps, and yet this clear shape that anyone can recognize, what on earth is this?"

"Ah. Don't you know? This is called a ‘letter.' It's used when writing."

Qing threw a blatant insult as she wrote the evaluations, but it did not reach Sima Chunfeng's ears.

Sima Chunfeng felt a deep sense of defeat.

The gap is so huge.

Even when she heard that Heavenly Blossom Sword had broken the record for the youngest Unrestrained Real master, which was unprecedented in history, Sima Chunfeng remained calm.

Because she was just a genius, and Heavenly Blossom Sword was a martial arts genius, so it was not shameful at all to be pushed aside in martial arts.

But letters were in the realm of literature.

And the handwriting is the essence of a dignified soul that expresses the spirit and fundamentals of that person.

"Sima-lang?"

"This can't be happening, this can't be happening."

"Young Lady Sima?"

"Ugh, this is my defeat, if I had to rate it, it's somewhere between one hundred and five, ugh, this is a complete defeat, a complete defeat……"

"Chun-feng?"

"This is unbeatable. No, Sima-lang, come to your senses. Nothing is impossible for this Sima-lang. No matter how magnificent her handwriting is, even if it's like a fortress, if that's the case, I'd rather emphasize its beauty by flowing it even more..."

Meanwhile, Nan-Gong Shencai left.

Of course, how could Nan-Gong Shencai alone accept so many applicants?

And the next person who took on the role of test tube is-

"This Daoist is called Changbin."

It was none other than the delinquent member and ghost member, Changbin!

Qing's gaze quickly turns from Sima Chunfeng, who was muttering incessantly, to Changbin.

No? That kid? Qing frowned.

\textit{No, if you're here, you should at least say hello and ask how I'm doing. Where the hell have you been, that you're only now sneaking your face in?}

\textit{Isn't he a very annoying guy?}

Of course, Changbin may feel wronged.

After arriving at the testing center, Changbin heard that Qing was staying there, but still?

'Is it really right for me to go greet her first? Heavenly Blossom Sword is a woman, so if a man from Daois Sect starts acting friendly, it won't look good to others. Even if people ask, 'What's that? Are you flirting with Heavenly Blossom Sword?', I have nothing to say. I'm just greeting her innocently, but what if others misunderstand that Heavenly Blossom Sword is flirting? And Heavenly Blossom Sword might not feel good about pretending to know me, and she might pretend to know me in front of other people without any tact. No, whether I'm close to Heavenly Blossom Sword or not, it seems like I am, but Heavenly Blossom Sword is kind to everyone, so she just treat me like anyone else. What if she misunderstands and starts acting friendly and stuff? At least we're on good terms now, so it's fortunate. And if that guy asks, 'What's that? Does he have any ulterior motives?' and then...'

That's right!

Changbin was the type of person who could never greet a woman first!

That doesn't mean Changbin hid on purpose.

He tried to find a natural encounter by wandering around, but he failed.

But in human history, isn't natural encounter a realm originally reserved for a select few individuals who naturally engage in conversation with the opposite sex and have exceptional sociability?

Of course, it is annoying that you don't know the circumstances.

\textit{You're done for. From today on, Changbin, you should learn to eat between me and Gunyeong. I'll make you sit down even if you have to sleep in my arms.}

"I also help you all- ahem."

Changbin had a strangely chilling premonition, and he coughed in vain as his hair stood on end, rubbing his arm.

Anyway, the sparring started.

After a while, the sparring ended.

Afterwards, warriors belonging to the Wulin Alliance's combat team came forward and sparred with the applicants.

While writing the evaluation, Qing realized something big.

\textit{Changming is a rare genius, no, not quite a genius, but a rare prodigy.}

Even though she was born with a strange constitution, Chen Changming entered Jianghu much too late.

\textit{Three years now? Four years? A proud Late-Stage First-Class realm. Well, the term 'Late-Stage First-Class ealm' is so absurd that it leaves me speechless, but is this a world where we have to divide First-Class into beginner, intermediate, and advanced? This is the end of the world, truly the end of the world.}

\textit{Still, it hasn't been long since she picked up the sword, and she's already at the First-Class Realm.}

\textit{Compared to that, if I look at this guys I have to teach, well, rather than Five Path Swordsmanship, shouldn't I just teach how to walk and how to hold a sword?}

\textit{More than that, um, my body feels a bit stiff. Slowly?}

Qing poked Sima Chunfeng in the side.

Kkwik. It was Sima Chunfeng, who rose an inch while still sitting. A mysterious technique! No, it was a slow technique since he jumped on his butt? Well, whatever.

It seemed that she was surprisingly weak to tickling.

"Wh-what is it?"

"Young Lady Sima, I'll get off on the next turn."

"…?"

"My skin's starting to tingle. I'm picking up a brush I've never used before, and what is this? I think I'll try moving my body around a bit."

Samarang's gaze then turned back to Qing's writing. "Is this a brush I've never used before?"

Then, a fire flashed in both eyes.

\textit{Yes, Heavenly Blossom Sword. This time, I'll count it as your victory. But, this Sima-lang won't be swayed by this defeat forever. I'll make you faint when you see my handwriting!}

That will never happen though.

Rather than being amazed by Sima Chunfeng's handwriting, it would have been impossible not to be amazed by Qing's well-written calligraphy even if the entire history of the three thousand worlds had passed together.

You might be surprised to see writing with food like noodles or meat, but wow, writing with food!

Anyway, Qing headed down to the observation deck.

Well, many teachers, no, even the principals, said that she could take sparring sessions whenever she wanted.

Rather, she was even asked if she could stand in front of a crowd at least once.

So, Heavenly Blossom Sword, enter the exam!
