\chapter{The New Semester Has Begun (3)}

"Sister, you brought such a beautiful niece here in the first place. Isn't that because you're planning to have her enter the Youth Division of the Yizheng Martial Study Hall? But if you become an instructor there, you'll inevitably end up being the subject of gossip."

In short, it's a question of favoritism.

"Why, why can't I just teach them all like my own children?"

"I know you're a very different person, Sister, so I know you wouldn't show favoritism. But isn't it possible that you might being too soft?"

"Not really? I'm taking the role of the father. I'm the epitome of strict, serious, and fearsome."

Zhuge Lixian looked at her.

To be exact, he was looking at the figure of Ciyu clinging tightly to a tree, like a cat.

And then sigh.

"Oh well, that's okay."

"What the heck, I felt so bad, just now-"

"Sister, you loved Xiang'er so much, so are you confident that you won't show favoritism to Xiang'er as the instructor of the Youth Division?"

"What, Xiang'er came? No, then you should've told me that first. Is Xiang'er also enrolling to the Youth Division? Do you think that little thing can swing a knife?"

"You've already started playing favorites."

"Well, Xiang'er is the cutest thing in the world. Isn't it enough to cherish a child who isn't yours without worrying about the consequences? It's the very definition of irresponsible pleasure."

He was a woman who was somehow sagging.

"No, Ciyu'er, are you jealous right now? Even if it's Ciyu'er, I can't lie. Xiang'er is the cutest in the world, but if I had to choose between the two, of course I'll choose Ciyu'er."

"Really?"

"Really."

"Really really?"

"Really, really, no, this is it. Did you learn it from Changming Mom? Are you teaching children to act cute?"

"what."

While Chen Changming answered like that, he smiled suspiciously, and Zhuge Lixian said, "Ahem."

"I understand that you like children, but that doesn't mean you're fit for the role of instructor."

"No, it's not that I like children, I just like their scent."

Yes, Qing didn't like children, she liked cute children.

A similar concept would be that the best dog was your friend's dog, and the best cat was your friend's friendly cat.

Of course, in the case of your friend's cat, it would be a bit difficult to observe it in the first place if it was unfamiliar to you.

"Hmm. I've even prepared a special training course for the young budding members of our martial arts sect. This was truly a once-in-a-lifetime opportunity, truly enriching and rewarding for them."

The curriculum for the boys' department prepared by Qing was a training of mind and body based on the theory of the past and present.

The main body of the Reverse Stream Sutra can be learned by oneself, but for the boys and girls of the youth division who will share at least some of its functions when they grow up, it was truly a special opportunity.

No, isn't it just fate itself?

"I heard that Monk Weifeng was taking charge of the youth department this time and will use the principles of the Yeokgeunsesu Gyeong to rectify the children's bones, muscles, and vital energy. Could there be a better educational program than that?"

"Ah."

It means that a real, skilled person with a strong sense of duty would be in charge of the task, not some idiot like Qing.

But if it's Weifeng, wasn't it that bald guy we faced in the semi-finals of the Jamryongbimuhoe?

I don't trust it much, no, not much…

Even so, it was also true that Qing was at a loss for words.

I'm thinking of teaching the same thing, but I can't say I'm better than that bald guy.

In the first place, you might ask how you know the principles of the Reverse Ten Thousand Years' Sutra, but you can't say that you learned it by just hearing it over someone's shoulder.

"Sister, since I'm not in a position to make any decisions anyway, let's unpack for now. You can contact the Academy Management Committee for further details. Since the Dagger Swordbreaker Master is currently out inspecting the state of the Academy, I think you should just relax and recover for now."

Zhuge Lixian came as a leader, not as an operator, so he wasn't in a position to do anything else as an instructor anyway.

Okay, let's unpack first.

In the first place, Qing didn't carry around that much luggage.

In fact, even if it wasn't Qing, the original warrior's bag was on the light side, so wouldn't it be light because there were no ronin, and wouldn't it be light because the warriors of the noble families could fill it with money?

And then, as expected, Qing rushed in to do what he had to do, which was to get a room, put his luggage down, and just lie there blankly.

Whether it's the world of martial arts or the hometown of Qing, once you enter the inn, don't you need time to just lie down and do nothing and adjust to the new environment?

Women lying sprawled out on the bed like that, um, but why did they all flock to my room and crawl into my not-so-large bed?

Still, it was nice to have the cool air in Gunyeong on a very hot spring day.

I didn't even lie down that long.

"Kuuuuu, Heavenly Blossom Sword? Are you here?"

A voice was heard along with the sound of the door opening briskly.

Is it normal to ask if someone was inside when opening a door?

A woman with unusually small, bean-sized pupils and four-white eyes with whites showing on both sides and above and below, giving her a strangely evil impression.

But rather than the eyes, a heavy mass about a head below them catches the eye.

The famous wisdom pouch of the Jinang Hyeonhwa.

Should I say that it draws your attention with an enormous suction power, or should I say that it feels like an irresistible pull?

If you actually see it, the force is, um, incredible.

"Young Lady Sima? What's going on?"

"How could I remain silent when the only person in the world who understands me, the destined friend of Bone Sima Rang, has come to visit? Surely Heavenly Blossom Sword felt the same way. So, there's no need to put on a show and wait, was there?"

Were we really that close?

I try to recall if there was any memory of us having spent time together, but it seems like it was just a few exchanges of greetings and a quick look.

But what.

However, Qing was not a person who would embarrass others by saying to their face, 'Aren't we still at the acquaintance stage?'

Rather, if you take it a step further, it gets even better.

If the other person was friendly first, I welcome it.

Moreover, Qing letters above his head were unusual, so there was no doubt that he was a person with a good influence here and there.

"Oh, you're not Samarang? Then, if a close friend asks for help, of course you should come running right away."

"You? Why were you suddenly on the level-"

"Oh, let's put aside all the pretense. Would you like to lie down? It's a bit cramped."

"No, why……?"

"Well, now that we're here, let's just lie down and think about what to do next. By the way, was there anything I need to register in advance for the entrance exam? Here's my younger brother, Jang Myeong. He's a senior disciple, so there aren't many his age. Oh, it's not like it's a favor or anything."

"If you're a disciple of the Divine Maiden Sect, then of course you're qualified. However, the leader position was already full, so I'm sure that's okay."

"How big was the position, Captain? Jang Myeong-ah? That's good. Come on, don't stand there. Lie down for a bit. Is there no space? Um, come here? Why don't you move over a bit?"

"Yes. No. I don't like it."

"Then long life-"

"I hate it too."

"We're not even finished talking. Okay, let's just sit next to each other a little bit. Make room for me."

It's a two-person bed, so they wiggle and wiggle, so somehow they stick together and make a space.

SamaChunfeng awkwardly lies down in the remaining space.

And then it was peaceful time again.

Ha-eum, when Qing yawns, a similar sound immediately echoes from within her arms.

I think I heard that yawning was contagious, biologically it's a mirror reaction, and scientifically it's because of the oxygen in the air, so if you're in the same space, it's the same condition, so there's this and that and stuff…

It was a moment when Qing, having missed out on all the important parts, was swallowing the worthless knowledge of his hometown and slowly giving himself over to the sleep that was creeping up on him, smiling faintly in a languid mood.

SamaChunfeng suddenly stood up and let out a strangely hearty laugh.

"Indeed, the Heavenly Sword! To think you were trying to shake up Sima Lang like this! I almost got caught up in it!"

Already lying in bed, the cold air from the human thermostat felt good. This was SamaChunfeng.

In other words, he was talking about getting involved in whatever he could.

"Huh, if I shake it, something will come out-"

"Indeed, he's an opponent you can't let your guard down against! As expected of Samarang's nemesis, he's no less capable."

She was a bit of a strange woman, then and now.

Well, it must be easy for a sane and good person to have such high karma in this primitive and ancient Zhongyuan.

"Yes! This time, I'll give it to you, I lost once! But next time, there's no way I'll be able to! Hehe, this defeat by Samarang, this thrilling sense of defeat that I rarely experience. Okay, okay. This was how it should be, then!"

And then he just backed away again.

What the? I guess he really just came to say hello.

After thinking that, Qing said, "Kulkul, what else in the world was as sweet as a nap?"

Dagger Sword Commander Yoo Seon-yeop was the head of the Wulin Alliance and has been assigned to the duties of the head of the Political and Martial Arts Academy during this semester.

If you say the internal commander of the Wulin Alliance, then in reality, it means the operator of the Wulin Alliance, the real power behind the scenes, or something similar.

He was the leader of the practitioners, completely different from the leader of the martial arts world who serves as a stamper and a face to greet guests.

Of course, I'm not saying that the leader of the martial arts world was a puppet.

I feel bad about bringing in a retired senior, but if I entrust him with work, I'm afraid he'll run away and say I'm not doing it, so I have separate staff. It's not like the president has any great power or anything.

"Meet the Yoo Dae-hyeop."

"Yes, the Heavenly Sword was still a force to be reckoned with. Unlike Hwagyeong's accomplishments, being an instructor must have been a burdensome decision. I appreciate your willingness to lend me your strength."

"What were you talking about? It's said that you only realize your shortcomings after learning, and that you can discuss difficulties after teaching. And it's also said that teaching was half the battle."

"Huh, I knew that my study of the Cheonhwa Sword was widely known throughout the world, but I didn't know that it was also profound in terms of scholarship."

The former was a passage from the Book of Rites, which says that teaching and learning grow together, and that a teacher grows through learning, and that therefore not only the learner but also the teacher learns.

The latter was a saying from the Ten Great Men of the Book of Documents, which means that teaching was half as effective as learning, because if you want to teach others, you must first deeply pursue that learning yourself.

Now, he was a blue-collar worker who can write letters easily.

This can be said to be a true miracle of the Academy.

"So, since I only intend to teach and utilize the officials for my own achievements, there was no need to express gratitude."

"Haha."

Yoo Seon-yeop's eyes were filled with even more affection.

It looked like he had already suffered fatal injuries from the sharp attacks of the old man's killer.

"As you say, to learn, you must first practice deeply. Here, take it. It's called the Oro Sword. It's also the martial art you must teach."

Qing accepts the emergency supplies and pretends to look them over.

Then, I called the martial arts instructor and checked the level, but, oh, it felt empty somehow.

What? No new martial arts?

Is this not a proper secret, or was it the rare Gong Dina? Like that strangely named martial art, it means it's still an unfinished martial art.

However, there was no way that the secret weapon given by the Wulin Alliance could be a fake, right?

"Oh, Elder Yoo Daehyeop? Is this by any chance an unfinished martial art?"

"You know that much after just one look? Wow! This is precisely why you achieved what you did. You are truly a gift from heaven!"

Yoo Seon-yeop was surprised.

\textit{I thought she was just going to glance at it, but how did she realize that the martial arts were incomplete?}

\textit{But what happened before my eyes had already happened, so doesn't that mean that this is the true nature of the Cheonhwa Sword?}

\textit{A true genius, no, a super genius, no, a super super genius, no, a super super super genius, a talent that would not be lacking even if you added the word "super" three times!}

Yoo Seon-yeop couldn't hide his amazement as if he had finally recognized the greatest feat of martial arts in history, one that would never be repeated again in the past or present.

When Chunfeng brought it up, Yoo Seon-yeop was against it, saying that more than half of the students would be older than Heavenly Blossom Sword, so how could Heavenly Blossom Sword be an instructor?

Now that he think about it, isn't this really a decision worth looking forward to?

However, Qing's heart sank.

\textit{Ah, I'm screwed.}

\textit{This thing can't be used at all.}