\chapter{The New Semester Has Begun (14)}

Qing's eyes scanned the stage sharply.

Of course, since we don't know the circumstances before and after, it's difficult to make a hasty judgment based solely on bad karma.

But considering the utilitarian nature of numbers, which prioritize results over process, this ultimately meant that they had caused significant harm.

"Please do me a favor."

However, Duan Diao, who was greeting the examiner, was a polite and well-mannered young man throughout the fight.

Hmm. An ambiguous guy appeared.

In fact, she could failed him any time.

The examiners had the unlimited power to grant special passes and special failures at their own discretion.

Although Qing felt that the scope of the examinator's right was too omnipotent, it was actually quite common in Zhongyuan.

In Zhongyuan, connections and favors were recognized as the proud abilities of an individual who was looked up to by many people.

This applies to both those who achieve their goals through connections and favors, and those who were in a position to accept favors.

Surprisingly, this practice was legal under the laws of Zhongyuan.

In fact, the act of wielding given authority for personal gain or profit has been an unjust and evil act since ancient times.

Even more surprisingly, the people of Zhongyuan proudly boasted about that abilities, saying things like 'I knew that man' or that 'I had helped him achieve this and that'.

Anyway.

If she wanted to drop it, she could.

But, was that okay?

What if the owner of a blood red Evil Karma was brazenly committing evil deeds right in front of Qing's eyes?

It would the opening of the exhibition of human body's mysteries with a practical exploration of the endurance limits of the human species and its incredible vitality.

But what if they're not doing anything stupid?

It's best to just not get involved.

To be exact, it doesn't really matter if they get involved with her, but they shouldn't get involved with her friends or acquaintances.

However, Qing couldn't reveal a very special eye that could quantify the karma of others.

It's not that Qing was a strange person.

If you really want to reveal the truth, there's nothing you can't reveal.

As she wandered around, she realized that Zhongyuan was full of strange people, and even if some of them had eyes that could see numbers on top of their heads, it wsn't particulary strange.

But, that shouldn't be the case.

The numbers that Qing saw couldn't really be an absolute standard, because they shouldn't be.

Because someone might asked Qing for a number and asked her to decide whether or not someone's worth killing.

Such important decisions were ones that you must decide for yourself and bear the consequences of.

Qing had no benefit to tell her friends or acquaintances.

So, Qing just wrote down the words on the evaluation form.

\begin{quote}
	Something seems suspicious. We request further investigation into his origins and background.
\end{quote}

\textit{He seems like a bad guy, but I'm not sure.}

\textit{Actually, Yizheng Martial Study Hall isn't my property or my almamater, so what else can I say? It's the Wulin Alliance affairs from now on.}

If she wrote it like this, they would at least investigate it, and if there was a problem, it will be filtered out.

Or what?

Since they're going to be admitted anyway, just watch closely to make sure they don't do anything strange.

"Wow, indeed, Heavenly Blossom Sword. You've given such a unique opinion. But what part of it was suspicious?"

Then, Sima Chunfeng, who had been looking at Qing's evaluation report, immediately showed her curiosity.

\textit{What the heck? Is there no privacy? Aren't evaluations supposed to be anonymous? If that's not the case, then why write them anonymously?}

\textit{But the handwriting cannot be hidden anyway, it will be obvious, and the person reading it will most likely be Chunfeng here, right?}

\textit{If she said she's going to see it later anyway, well, what?}

'By the way, I am a little curious about your previous assessment.'

So Qing had no choice but to answer.

"Because I have a strange feeling? There's no particular reason, it just feels a little strange?"

"Indeed! For geniuses like us, feelings aren't just feelings. Hmm, if it's Heavenly Blossom Sword's opinion, then I shouldn't take it lightly. Now that I think about it, even I find it a bit suspicious. No, let's say this Sima-lang felt something cold first. There's no way this Sima-lang couldn't have sensed what Heavenly Blossom Sword felt. Hmm, yes, that's right, he looks very ordinary. So ordinary. How can he look so ordinary? It's truly very suspicious."

\textit{Is this a contest to see who can find something suspicious?}

\textit{Still, I'm a little grateful that she readily agreed when I said that it was just a feeling, even though it was basically based on the blind faith of her own so-called genius.}

First day of exam was over.

Because the day was based on the sun, not the low hours of Zhongyuan, it got longer as summer approaches.

In fact, this is the time before mankind could overcome the night, not just in Zhongyuan but anywhere in the modern era.

What this meant was that the time between lunch and dinner was slowly getting longer.

"Ugh, I'm hungry."

It's not that she's actually hungry, it's that it's already too late, so a loud rumbling occured in her empty stomach.

Sima Chunfeng thougt about the amount of food Qing ate for lunch, a meal that seemed to test the limits of her body, and quietly mused to herself, 'Hmm, what on earth is this stomach?'

But there's nothing Qing could do about it.

Isn't the gift of the Eonyeong, the Saengsimgyeol, a martial art that provides abundant vitality while preserving more food intake, a martial art with only advantages?

It increased the daily food intake, which was a limited resource, by about one meal!

Being able to eat one more meal was truly a supreme feat, something that could hardly be considered a red border.

"Chunfeng, are you going to eat too? Hmm, what should I eat? I think it's because you mentioned Xishi-niu earlier, but I've been wanting to talk to you. Would you let me?"

"Heavenly Blossom Sword? Where are you looking when you talk?"

Xishi-niu refers to the raw fish of the yellow puffer, which was the most precious of all pufferfish.

It was said that there was nothing in the world more delicious and tastier than this white and soft meat, so it was called Xishi-niu, or Xishi's milk.

It was a naming method that would make even Xishi trembled.

Of course, the person who named it may also feel wronged.

Xi Shi was the most successful example of seduction, and she actually led the King of Wu to pleasure, ultimately leading to the downfall of the state. (Diao Chan was a purely fictional character by Luo Guanzhong, not a real person, but modeled after Xi Shi.)

So, she was the most beautiful woman in history, but she was also a poison that destroyed the country.

So the most delicious part of the poisonous pufferfish was the most delicious part of the poisonous poem-

Correction. You have no right to feel wronged.

"Come on, let's go eat quickly. I told you, we're about to have the meeting of the century between our stomachs and backs."

"Ahem, Heavenly Blossom Sword. Superhumans like us, like General Xiang Yu, possessing the same short-range, universally omnipotent abilities, have a correspondingly high level of responsibility. While a mere soldier can take on one enemy, we superhumans on Hanhyeol horses must face ten thousand before we're truly qualified to care for such low-level mediocrities, right?"

"The noise is getting louder and louder. Anyway, it's fun, so keep going."

"Nonsense! No, no, haha, Heavenly Blossom Sword, you always try to shake Sima-lang like that, trying to find a weak point? But I already saw through it, didn't I? In fact, it's a tactic that won't work on Sima-lang, who always lives amidst the envy and jealousy of ordinary people."

"Okay. What's the conclusion? Are you going to eat?"

"The military's work was just beginning. If we don't organize these evaluations and reach a conclusion by today, won't the results of the ongoing primary tests continue to drift indefinitely further away?"

"Ah. You have to go to work…"

Qing looked at her with a pitiful expression.

It's not that it wasn't true, but the expressions on the faces of the Military Division officers among the evaluators were all rotten.

Well, the paperwork starts now.

"Chunfeng, you go eat."

"Chunfeng, you should eat with your friends too. No, no, you must eat with your friends."

"Chunfeng'er. You always made a fuss asking when the Cheonhwa Sword would come, and now that the one you longed for has come, you should feed each other warmly."

"Who, who was making a fuss, and how many times must I, Sima-lang, tell you not to call the name of Sima-lang so carelessly…!"

\textit{Hmm. She doesn't have any friends either. That's not surprising at all. Actually, I'd been thinking that would be the case for a while now.}

\textit{Why do only friendsless people gather around me?}

\textit{Well, I'm a savior of the friendless and I do some good deeds of giving them friendship, but, oh, is that why?}

"Come on, just eating a meal isn't going to make your evaluation disappear. We're just trying to eat and live. Should we start by eating?"

"No. These ordinary men wouldn't be able to finish on time even if they stayed up all night without the main woman. All these ordinary soldiers combined were only half as skilled as Sima-lang, so it would be gross negligence for the main character to be absent."

The expressions on the faces of the ordinary people listening became even more rotten.

However, even though the words were harsh, the meaning itself was that she will ultimately help the Military Division.

\textit{The kid was a bit strange, no, very strange, but I think she has a lot of virtue. Although she has some shortcomings, I think she has a good personality.}

"Heavenly Blossom Sword? I know it's a terrible thing, but can you please take this person away? She just finished her part and then set a snack table in front of the office to have fun. She just munched on bamboo leaf jong (rice balls) and finishing quickly, and then she's like, "Oh, sorry, about that' in front of the workers, and it's hard to describe it other than that. She's so annoying, she's the most annoying person I've ever seen."

"Well, it doesn't erase the fact this Sima-lang processes more than three times as many documents as you do, does it?"

"See, look at that. No matter what I say, she won't listen to those swear words."

The military officer sighs deeply.

Qing took a moment to compose her speech, wondering what this meant.

"Let me gethis right. Are you saying she skipped dinner for the sole purpose of finishing work quickly and just laze around in front of everyone, especially the people she's working with? Of course, she also do more work to do than everyone else, so you have nothing to say, and that makes it even more unpleasant to see?"

"That's very accurate."

"Hmm. The more I learn, the more amazed I become."

"Every day was a series of surprises for us too."

The Military Division officers nodded heavily.

Qing grabbed Sima Chunfeng's wrist.

"Okay, let's go eat dinner. You have to eat it's the time to eat. It's not good to eat while working."

"Oh, you don't understand what I'm saying? The Heavenly Sword, people like us—"

"Okay."

Qing suddenly grabs Sima Chunfeng's slender wrist.

As expected of a brainiac, she was incredibly weak. She was so weak that it was almost embarrassing to call her a warrior. How could she overcome that miraculous power that rivaled General Xiang Yu?

Sima Chunfeng's body, which was being carried into Qing's arms, turned half a turn, ands he wrapped both arms tightly around her waist.

Subjugation complete. Weakness exploited.

"Heavenly Blossom Sword? What the, kkahak, keut, kkiiyathat! Ugh, keuhreut!"

Qing was gently rubbing her sides while wrapping her arms around her waist.

Usually, the opponent's waist was wrapped around both arms to restrain them so tightly that they cannot move at all.

Because I have already learned through experience that even if you release both your arms, it will only shut my mouth and not flap its wings.

On the one hand, it's a bit absurd.

Is there any reason to be so desperate to suppress your voice? Judging by your words and actions today, you're clearly mentally unstable. Haven't you already lost all sense of dignity?

"Want to go eat? Want to keep having fun?"

"Ugh, not at all, hoo, not fun, hoo, hoo, but this Sima-lang, hoo, doesn't give in to such threats, kkuht, keuht, puhahak, kyahat-"

Qing thought as he poked and prodded Sima Chunfeng's weak points, which were fluttering vigorously like a live fish just caught in his arms.

What the heck is this? This tingling sensation, this reaction?

Also, her stubbornness was so strong that she doesn't give in, which was really unbearable.

Qing lifts Sima Chunfeng into the air and goes down to the observation deck.

Although Sima Chunfeng is a tall woman, about a finger-width shorter than Qing (though slightly taller when sitting), in reality, with Qing's strength and stamina, he cannot even lift this much weight.

Should we say it was below the critical point or the limit?

When a person carries a sack of rice, their heart starts racing and they start breathing heavily, but when they carry an empty basket, there was no loss of physical strength or energy.

"Whew, Heavenly Blossom Sword? I, the one who has to process the evaluation report, kekekeke! Stop it, hickey."

"Whew, Heavenly Blossom Sword, you can carry a horse to the waterside, but you can't make it drink water!"

"Heavenly Blossom Sword, gasp, huh, I, absolutely, this, huh, huh, huh, huh, I will not yield to oppression, huh. Kkeup-!"

Sima Chunfeng was just as strong-willed.

Every time he spoke nonsense like that, Qing would stab his side, causing a loud spasm and a shrill scream as he headed to the banquet hall.
