\chapter{Transcendent Qing(2)}

Honestly, there was no particular reason for Qing to tease the two of
them. If there was a slight reason, it would be that their reactions were
so amusing that she found it fun to mess with them.

If it had been Gong Sonye, and she had said 'I am Transcendent Qing',
all she would have said was 'Wow. Young Lady Ximen is truly amazing.',
which would have been really boring.

Moreover, it seemed like she had been beaten quite badly when she had
fallen into a state of selflessness, so she felt both grateful and sorry. It
was fortunate that they used blunt training swords; otherwise, Gong
Sonye would have been split into four pieces, and her limbs would have
been chopped off, thus torn to shreds.

And Dang Nana wouldn't even let herself be hit even if Qing tried.

The Tang Clan, unofficially allied with the royal household, even
possessed firearms, making them de facto the most powerful family in
the current era of Zhongyuan.

With the firepower of those firearms, as well as the ability to load and
fire poison, the daughter of such a formidable family had no regard for
personal skill.

As such, Qing actively sought out targets to vent her frustrations on.

Honestly, there were quite a number of them if she just went to the
Hidden Dragon Assembly.

Look at them, drinking alcohol and tea like they have all the time in the
world when they're barely in the Peak Realm.

When I was at the Peak Realm, I didn't sleep or eat and only swung my
sword all day. Well, not really, but still.

"Yo. Isn't that Changbin?"

"Gasp, Gra, Grand Master, Grand Master is here……"

"What the. Why are you so stiff again? Haven't seen me in a while, so
you're being all difficult again?"

"That's not it. The Sect Leader keeps calling Young Lady 'My Youngest
Junior Sister'. He keeps saying that, so, I, uh, I can't dare to."

As he sneaked glances at her, Qing grinned and replied.

"Hey, we're friends, aren't we? It seems like Sect Leader Yuha likes me,
so what? How can I be a Grand Master to a Mount Hua disciple? Relax.
Be comfortable."

"Uh, um. Then, that's……"

"But let's get this straight. We were friends. I don't care about seniority.
But don't think about trying to compete with a Transcendent Realm
Master. A martial artist should speak with martial arts, shouldn't they?"

"Uh…… Then, what should this lowly one call you?"

As Changbin was stammering, Qing sighed deeply.

He's hopeless too.

I guess it can't be helped since he can't even meet my eyes in the first
place.

"Aigo, I can't make a joke around Changbin. Be a bit more comfortable,
okay? Like a real man? Hm? It's been a while since we became friends,
but you're still acting like a stranger?"

"I-It's comfortable. Really comfortable……"

"Alright. That's enough. Pour me a drink."

Since a woman had joined the group, Changbin had been sipping the
very, very delicious alcohol sparingly, as if rationing it.

Regardless, after Qing filled her glass, she looked around.

The bastard I wanted to tease isn't here. Instead, I just keep making eye
contact with other men.

Hm. Should I have worn a veil?

I didn't wear one because I've already shown my face, but now
everyone's staring holes into me.

One peculiar thing was that the five brothers of the Tang Clan did not
display their usual fervent kindness.

This was because, to the men of Zhongyuan, a woman more
powerful than them was very burdensome.

Later, they would have to marry, have concubines, and enjoy a life of
leisure with three wives and four concubines. But if their wife was a
Master, forget about having concubines; they would be lucky to not get
beaten.

This went directly against the unspoken agreement of the Central
Plains.

In love, it was all about being a simp. The man had to give everything,
including his heart.

However, after marriage, it was all about male chauvinism. The most
beloved woman among the three wives and four concubines would be
the one who was doted on the most, thus requiring her to compete
with the others to be coquettish and alluring.

While Qing was looking around, one beauty caught her eye.

Her skin was so pale it was almost ashen, and her expression seemed
melancholic yet indifferent.

However, the beauty mark under her eye was so alluring that Qing
inadvertently swallowed her saliva.

It was the Snow Flower, Young Lady Seol Yiri.

Qing tapped Changbin's shoulder and then quietly approached the
Snow Flower.

As she took a seat on the opposite side, an indifferent gaze flew
straight at Qing.

Qing grinned and greeted her.

"Hello there? Uh, are you Young Lady Seol Yiri, the Snow Flower? My
name is Ximen Qing."

"Yes."

Qing's words were cut off.

Would someone normally answer with just 'Yes'?

And what was 'Yes' even in response to? Was she saying hello? Was she
confirming she was the Snow Flower? Or did she know that Qing was
Ximen Qing?

While Qing was struggling to find her bearings…

"Your business."

"Yes?"

"What is your business with me?"

Qing smiled and tapped the table.

"Nothing much. I just wanted to greet you. As soon as I saw Young Lady
Seol, I just thought, wow, she's pretty, so pretty that I wanted to get
close to her. Wow, you're even prettier up close."

"Yes."

Another blunt reply.

It felt as if some mysterious power that blocked people's words
dwelled within that single syllable.

As such, while looking at Qing, who was at a loss for words due to this
mysterious power, Seol Yiri opened her lips.

"Do you have anything more to say?"

It was usually a line used to tell someone to get lost when there was
nothing more to see.

A very cold wind blew.

"Um. Did I perhaps commit some rudeness?"

"No."

"Is there anything you don't like about me?"

"No."

"Then, do you not want to talk with me?"

"Yes."

Then, Seol Yiri closed her mouth tightly.

It seemed like the title Snow Flower wasn't just for show. It felt like
talking to a mirror would be more productive.

Ah shit, it's not easy to return this martial art.

Wasn't it Seolganom who asked her to return the Supreme Yin Jade
Maiden Divine Art to the Ice Palace if she ever met someone from
there?

Since she heard that Seol Yiri was from the Ice Palace, she tried to
inquire about it, but…

Then, a teapot suddenly caught her eye.

Qing grinned and tilted the teapot.

The unique scent of Longjing tea wafted cozily. This was because the
tea was hot, with steam rising from it.

Qing raised her Inner Qi and cooled the tea until frost formed.

It was the cold Longjing tea that Qing liked.

Since she was from the Korean Peninsula…

The Korean people were human beings who would drink brewed, burnt
beans with half a cup of ice even during an ice age that brought about
the extinction of mankind.

On the other hand, for the people of Zhongyuan, who had a very
scientific idea that any liquid that entered the mouth must be hot,
otherwise it would be very harmful to the body, this was an act akin to
a crime that would shock all under Heaven.

At such an atrocity, Seol Yiri's eyes widened.

"Just now…"

"Oh, you know about this! This is called the Supreme Yin Jade Maiden
Divine Art. It's really, really coooooold. Just like Young Lady Seol's
attitude."

"How, how do you know that?!"

"Does it matter how? What matters is that I have the Secret Manual for
the Supreme Yin Jade Maiden Divine Art and that I was asked to return
it to the people of the Ice Palace."

"Who, who made such a request?"

"Well. To protect the identity of the informant, the person shall remain
strictly anonymous. I was allowed to learn it on the condition that I
return it, so don't question me on tha-"

"Seolganom. That bastard, wasn't it?"

Seol Yiri interrupted Qing and exclaimed urgently.

A cold aura emanated from her chilly tone, causing Qing to immediately
make an assessment.

It seems like they're acquaintances with a bad relationship.

"That scoundrel is a sinner of the Ice Palace. Not only did he kill his
master and his fellow disciples, but he also set fire to the sect and ran
away. He is a heinous Demonic Adept."

"Well, I'm not going to reveal the identity of the informant. Anyway, I'll
transcribe the Secret Manual by tomorrow, no, the day after tomorrow,
so just be aware of that."

If she stayed any longer, she felt like she would just end up telling more
and more lies. Moreover, from the sound of it, it seemed like she had a
lot of animosity with Seolganom. It would be best to not get too close to
her, otherwise it might lead to unnecessary disputes.

Ugh. I wanted to get close with Young Lady Seol.

But what can I do? It is not a true man's deed to abandon friendship for
the sake of seducing women.

I guess I'll have to give up with tears in my eyes.

But why is it that every woman I like is either the final boss or my
friend's enemy?

Is there some sort of curse on frail and pitiful characters or something……

Qing let go of her lingering feelings and stood up.

However, it seemed like Seol Yiri couldn't let go of her lingering
feelings. Moreover, she even expressed those feelings quite overtly.
Seol Yiri's gaze was fixed directly on Qing.

Even though human eyes had the function to roll around and look at
their surroundings, her pretty face was only directed at Qing.

It was like an owl or a falcon, or whatever those birds of prey were. A
face without any expression, chasing after Qing, was a bit scary, no
matter how much it it her tastes.

No, should I say that my tastes are being shattered?

As Qing shuddered, it was then…

"Qingah, you know, Grandfather saw a very interesting blacksmith at the
market and wants to buy a few daggers. Let's go toge-, what's wrong?
Qing, what did you do to Seolhwa?"

"I just tried to talk to her and she was so cold that I gave up."

"What, you, again. Are you trying to drag Seolhwa to bed this time?"

"What do you mean by that………"

Although it was strange to only hear the words, it didn't sound that
strange when the tone was added.

It was because her voice was full of laughter, so it sounded like she was
joking around.

"But why is she like that? Isn't she staring too much? If you have
something to say, just say it. Ugh, it's a bit scary, though."

"I also think so. I never expected her to have such a persistent side to
her."

She seemed like the type to just coldly reject any requests for
conversation, so I thought that was just how she was, but I guess a
person's true nature can only be known after experiencing it.

Who knew she would stare so blatantly and openly? I'm getting
goosebumps.

"Mmm. I guess it can't be helped."

Qing declared her retreat.

I can't show off like this. It's my first time reaching the Transcendent
Realm, so why can't I show off? I have to spread the great achievements
of the great Transcendent Qing far and wide, so everyone can look up to
me.

With a sad heart, Qing put aside her wholesome plan to motivate and
encourage the late bloomers by instilling a sense of crisis and a desire
for self-improvement.

Let's just go back today and work hard on transcribing the Supreme Yin
Jade Maiden Divine Art.

On the way back, Dang Nana was being noisy again.

"What, Qing, why are you walking like that?"

"Huh? What do you mean?"

"Why are you walking so lewdly? Ha. You're already carrying two
mooncakes around, but you still do this. I can't even. Is this why you
change women every night? Fine, just tell me. Is it me or Gong Sonye?
Who's better in bed?"

"If I had to pick, it's the latter. At least she doesn't grope me."

"I don't grope you anymore, though?"

"It's not that you don't grope me anymore, it's that you can't. Be honest.
How much did you enjoy touching me while I was sleeping, huh?"

Thanks to her senses that had blossomed due to the Realization Divine
Art, she had been waking up constantly from Dang Nana's impure
touch.

After waking up more than ten times, even Qing couldn't help but get
angry and yell at her to let her sleep.

"Th-That's not it! It was just a natural hand movement, you know?
While sleeping. Ju-Just a very natural movement, yes, that's right."

Even while saying so, she couldn't meet Qing's eyes. Qing narrowed her
eyes at her.

As a result, the topic of Qing's lewd gait was pushed aside.

Honestly, Qing was just trying to walk quietly, so she had no idea what
her gait was like.

In the primitive ancient times of Zhongyuan, technology was
uncivilized, so there were no smooth surfaces where one's appearance
could be reflected. Glass itself was a rare item.

Thus, one could not experience the awkwardness of approaching a car
or a glass wall of a building to fix one's hair, only to make eye contact
with the person inside, like in Qing's hometown.

And Qing was the first female Divine Thief in history, so

Cheonyu Hak had no reaction other than reminiscing, 'Ah, I was like that
too', upon seeing his disciple's appearance.

As for Ximen Surin's nagging, she was so strict about the conduct of
beautiful women that Qing just assumed she couldn't accept her
walking on her tiptoes.

Anyway, as they were bickering like that, they entered Mucheon
Pavilion, where a servant greeted Qing and delivered the news.

She said there was a guest waiting inside. 