\chapter{Transcendent Qing(4)}
Sima Chunbong always feels lonely.

Yes, loneliness.

It's the curse of having a mind far too brilliant.

What others struggle with, fumbling around in confusion, she can grasp at a single glance.

And that's why she has no one to walk alongside her.

Too lonely.

Even if she slows her pace to a crawl, reducing her stride to an infuriatingly sluggish shuffle, no one can keep up.

Yes. Among the sparrows, she is the lone crane.

No matter how desperately the little birds flutter their wings, they cannot keep up with a single powerful beat of the crane's wings.

And this graceful crane is none other than herself...

“Ohhh. How terribly lonely I am.”

Her subordinate, Assistant Military Strategist Kang Jihwang, clicked his tongue.

“There she goes again, spouting nonsense. If you've got nothing better to do, go pick out some candidates for the Military Instruction Department instructors.”

“Didn't you see the stack on your desk? I've already narrowed it down for you. Well, with your abilities, Assistant Strategist, you might have to pull an all-nighter. Fufufu.”

A vein bulged on Kang Jihwang's forehead.

If she weren't so competent, he'd tear her a new one.

But it's not like she doesn't work. No matter what he tells her to do, it always ends up neatly on his desk, as if some ghost had done it for her.

Sima Chunbong, assuming what she believed was a graceful and enigmatic posture, perched herself on the windowsill of the military office, gazing wistfully outside with what she thought was a melancholic look.

“I often wonder... perhaps I am not like other humans. No, perhaps I am something fundamentally different. If they are humans, then I must be a god. If I am human, then they are mere monkeys...”

Kang Jihwang shook his head.

“This is all the General's fault, isn't it?”

“How is it my fault that the kid was born with such an odd disposition?”

“Well, you did give her that name. I mean, isn't it obvious she'd turn out a bit... off? I'd bet she hates her name.”

“What's wrong with Chunbong? Chun, it sounds like the blossoming of spring flowers. And Bong? Do I really need to explain why a phoenix is a good name?”

“But you combined them...”

“If you put a good thing together with another good thing, doesn't it make an even better thing? I put a good name with another good name, so of course it's a doubly good name.”

“Hm. I'm not so sure about Sima Chun or Sima Bong being great names either. But at least I now understand that you should never be allowed to name anyone ever again.”

“Oh, come on, Pildeok turned out fine.”

“Hmm.”

Kang Jihwang pressed his lips together.

The last time Sima Pildeok got drunk, he'd seriously asked if he could join one of the Nine Great Sects just to get a new name.

Meanwhile, Sima Chunbong remained lost in her own little world.

I am a lone crane, soaring proudly and alone, but even I sometimes need someone to keep in step with me.

Even I feel lonely sometimes...

“Yes. Perhaps... him.”

Sima Chunbong thought of the newly risen prodigy of the Orthodox Wulin.

First off, he was a beauty.

Those cat-like eyes, those slightly pouty lips that formed a soft curve.

Judging by his face, he had that classic, cold-hearted, sharp-tongued, unyielding personality that wouldn't listen to a damn thing anyone said.

But it couldn't be helped.

The world that young genius perceived must be just as stifling as the one Sima Chunbong constantly felt — a world that stifled geniuses until they abandoned any hope of being understood.

Nevertheless, his abilities were outstanding.

Another commonality between them — to be both beautiful and talented, a genius of the century.

Yet despite that, he hadn't forsaken his duties.

While others would have sung their own praises, he chose instead to use his abilities for the poor and the destitute without announcing it.

Unlike the common rabble, he carried out the mission bestowed upon geniuses hand-crafted by Nüwa herself, using his talents to better the world.

Just like her!

A glimmer of light returned to Sima Chunbong's eyes.

“Maybe... just maybe...!”

But Nüwa is a cruel deity.

She had created such perfection and yet attached a single fatal flaw, a piece of useless, humiliating flesh.

Yes, the prodigy shared her suffering.

It was as if Nüwa had wept as she added that defect, forced to balance out her creation so that no one could be too perfect.

A mark of genius, or perhaps the curse of genius!

If that was true, then her own flaw made perfect sense as well!

“Yes. Even someone like me needs at least one person to stand shoulder-to-shoulder with...”

Sima Chunbong did not hesitate.

For she had absolute confidence in her judgment and never considered the possibility of being wrong.

With that, she jumped down from the windowsill.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Moyong Juhee lay sprawled on the floor, twitching.

Qing knew that feeling all too well, as a fellow victim of such an impact.

Getting hit like that...

Yeah. The expression “my mind went blank” couldn't be more accurate.

Your mind becomes a pure white canvas as you roll around on the floor like a rag doll.

But the impact was perfectly controlled. Shouldn't she be getting up by now?

The sensation transferred through the second knuckle of her middle finger was flawless.

There was no split scalp, no cracked skull.

What Qing failed to account for was that she had already developed a certain tolerance to those ⊛ Nоvеlιght ⊛ (Read the full story) nuclear forehead flicks after multiple exposures.

For Moyong Juhee, however, it was a whole new world.

The ultimate weapon, the harbinger of the apocalypse, the destroyer of worlds — she'd been struck by it.

Thus, Qing looked down at Moyong Juhee, who was writhing on the ground, silently screaming.

Something about her wriggling like that was...

Well, kind of pitiful but also strangely captivating.

Qing didn't realize it, but her lips had already curved into a soft, graceful arc.

“Stop being so dramatic and get up.”

“It's not drama... Agh...”

“Come here.”

Qing lightly patted her lap.

Moyong Juhee obediently crawled back into her embrace.

Qing firmly pressed her hand against the impact point, gently massaging it.

“Aah...”

Moyong Juhee let out an involuntary sound.

The coolness of Qing's hand as it caressed her scalp was incredibly soothing.

And the voice whispering so softly in her ear...

“There. We both hurt each other a lot, so no more grudges between us, okay?”

“Th-this isn't what I meant...”

“And stay over tonight.”

Moyong Juhee shook her head firmly.

Qing ran her hand over Moyong Juhee's hair, feeling around. Hmm, was this a bump? It was definitely protruding.

“I'm fine. If I keep whining, I'll never get better. I'm going to try to endure it as much as I can. So...”

It was a commendable thing to say.

But it was also incredibly foolish, so Qing cut her off.

“Oh, come on. You're clearly not fine. Look at those dark circles under your eyes. You said you couldn't sleep alone, right? Actually, I feel the same way. When I'm alone, I can't close my eyes either.”

“But why? You're so strong, Lady Ximen. You're even at the Transcendent Level now, and beyond that, you have such a strong heart...”

“There's no way that's true. I get scared and tired too. But... I keep going because I believe that if I endure it, something good will eventually happen.”

It was a realization she'd come to after crossing the wall.

She had feared that there would be something terrible waiting on the other side, but when she finally broke through, all she found was a road that stretched endlessly into the distance.

So even now, she still felt anxious.

When she closed her eyes alone, she couldn't shake the fear that she'd wake up to find it was all a dream — that she was still trapped in that cave somewhere in Liaoning.

But what choice did she have? She had to endure.

If she just kept holding on, she would keep advancing through the stages — Transcendent, Heavenly, Life and Death — and eventually shatter the illusionary walls of the system.

Besides, if you can't sleep alone, you can always sleep together.

“There's no need to make yourself suffer just to endure it. If there's a way to make it easier on yourself, you should take it. The important thing is to keep going, right?”

“Th-thank you. Truly, for being so kind to someone like me... to such a worthless and wretched girl like me.”

Why is her self-esteem so low?

Was she always like this?

Now that she thought about it, she probably was.

Someone with confidence wouldn't keep comparing themselves to others, exposing their insecurities like that.

Yeah, from the very start, she'd been a worthless and wretched girl.

But then again, if she thought about it that way, her martial sisters were... hmm, no, that wasn't quite right. They were just a bunch of delinquents who had learned bad habits from watching Qing.

Nana was the youngest and weakest, but she'd ended up taking care of them instead of being spoiled.

She might be a pathetic girl, but she wasn't a wicked one.

And Nana, well, she was a respected doctor from the start.

Not pathetic, not wicked.

San? From the very beginning, he'd been full of himself, strutting around.

Namgung Sinjae? He was a carefree, good-natured guy whose only flaw was his lack of talent.

Hmm, who else?

Anyone who was pathetic and wicked?

Gramps? But he had dementia, so he couldn't help it.

Besides, he was a demonic cultivator, but he was still talented.

Seolga? He'd been extraordinary from the moment they met.

Just thinking about it made her feel proud — the neighborhood's top genius!

Thinking over all her connections, her masters had both been exceptional.

Or, even if they had flaws, it was always just one side, not both.

“Now that I think about it, Miss Moyong does have a bit of that in her.”

“Lady Ximen?”

“I'm just kidding. It's fine. Sure, she might be a complete mess right now, but what's important is that she's trying to become a better person, right? If you keep moving forward, even just one step a day, you'll eventually look back and see how far you've come.”

Qing said some vaguely inspirational lines she'd heard somewhere before.

“A complete mess right now...”

And that's when it happened.

—“Deputy Strategist? No matter how high-ranking you are, you can't just barge into Mucheon Pavilion...!”

—“Out of my way, you little brats. This lady is coming through, and none of you can stop me. Here, take this.”

—“Ah! The Glorious Hall's Seven Treasures Soup...!”

—“Hah, at least you have good taste. Now, don't block the path of a distinguished guest. All you ever do is drool over the snacks we serve the VIPs, right? Here, eat up and scram.”

There was a commotion outside, and then — BAM! — the double doors to the Mucheon Pavilion's reception room swung open.

Standing dead center in the open doorway was a woman with her legs spread wide in a grand, bold stance.

Qing, who had been sitting with Moyong Juhee, looked over to see just what kind of noisy guest had arrived.

First impression: A beauty, but... a bad one.

She looked like trouble. Definitely had the face of a villain or a schemer.

Her eyes were so large they seemed disproportionate, showing too much white on all four sides.

In physiognomy, that was called a “Four Whites Eye,” the worst type of eye shape, a trait ascribed to those considered vicious and dangerous, more beast than human.

But, as filthy as the world was, even with such wicked eyes, she was still beautiful.

Her attire was no less striking.

A dazzling crimson silk robe embroidered with gold threads in a pattern so convoluted it defied description, shimmering with a complex, almost metaphysical design.

Ornate and resplendent. Utterly excessive.

“Ah. There you are, Lady Ximen! I am Sima Rang, the one people revere as the Wise Blossom, Hyunhwa. And what's going on here? Why is the Sword Blossom lying beneath you?”

“You—”

“Oh, but I guess it doesn't matter. It's not like ordinary people could understand the ways of us geniuses, right? Lady Ximen? Hello. I am Sima Rang, the Wise Blossom...”

She greeted Qing again, completely disregarding Moyong Juhee as if she were invisible.

“Ah. Yes. Hello,” Qing said, a bit flustered.

Um, do people normally call themselves wise and revered like that?

One? Two? Oops, that was almost rude of me.

“Zhinan Xianhua! (Wisdom Pouch Flower)” 

She was a bit late, but Qing still managed to keep up the customary pleasantries of the martial world.