\chapter{Transcendent Qing(1)}

In addition to her title, Qing also received a badge.

It was a blue badge with the character '長' written on it, which was worn by the group leaders of the Heavenly Martial Team.

The Dragon and Phoenix Assembly was not just a social gathering for the next generation of leaders of the Orthodox Faction. It was also an official combat unit under the Wulin Alliance.

Thus, the rising stars of the Orthodox Faction were assigned to the Heavenly Martial Team and the Earthly Courage Team, reserve combat units under the Wulin Alliance.

Officially, these two were equal and independent combat units, with no hierarchy between them.

However, those with outstanding skills, or those who came from the Nine Great Sects and Ten Great Families or had a backing of similar stature, were assigned to the Heavenly Martial Team. And the rest, the leftovers, were assigned to the Earthly Courage Team.

According to the Wulin Alliance, they were absolutely not divided based on status or backing. They claimed that this division was merely based on the need for additional guidance.

Young martial artists who already possessed a martial arts system and did not need external guidance were placed in the Heavenly Martial Team.

In contrast, the Earthly Courage Team was provided with advanced martial arts and personalized guidance from the masters of the Wulin Alliance.

Of course, this was the official stance.

The initial intention might have been such.

However, the young martial artists, who were still immature, in other words, naive, mostly didn't think that way.

The members of the Heavenly Martial Team actually considered themselves as hostages held by the Nine Great Sects and Ten Great Families. As such, they found the activities of the Heavenly Martial Team extremely bothersome.

The advice given to members of the Heavenly Martial Team was to avoid any event if possible.

On the other hand, the members of the Earthly Courage Team were eager to build up their skills and reputation to enter the Heavenly Martial Team. So, when a mission occasionally came down, they would volunteer in droves.

This was the glorious Heavenly Martial Team, but Qing was not at all pleased with it.

A combat unit might sound impressive when it's called the Heavenly Martial Team, but wasn't it just an army?

And as a discharged soldier, as well as a beautiful girl, I know that armies have a tendency to name their combat units with cool names.

It makes the soldiers feel a sense of belonging and maintains morale.

But no matter how good it sounds, an army is an army. I absolutely refuse to go through that shit twice.

"Master, do I really have to participate in this Heavenly Martial Team or whatever it is?"

"Do not worry, my disciple. It is not as formal a group as you might think. After all, what can the Wulin Alliance even do? How could they possibly boss around the scions of prestigious families? Unless there is a major incident in Murim, you will not be forced to take on any missions."

Just look at the members of the Anti-Sword Alliance. Both Peng Daesan and Namgung Shinjae were part of the Heavenly Martial Team. The heirs of the Five Great Families were firmly within it.

So, if they were assigned a dangerous mission and got hurt, the Wulin Alliance could not handle the ensuing resentment.

Therefore, the missions that actually came down were mostly like, 'Someone is going somewhere, so please escort (accompany) them'. Or, 'Someone is holding a feast somewhere, so please attend and leave the three characters of Wulin Alliance in the guest book'.

Rather than missions, it was more about assisting the journeys of these esteemed scions.

"Mm. But still."

"However, my disciple, you have already won the Hidden Dragon Martial Competition. For the sake of the Wulin Alliance's face, you must understand."

To be frank, a disciple of the Divine Maiden Sect was not qualified to enter the Heavenly Martial Team.

The Divine Maiden Sect was only famous for being a mysterious sect composed solely of women. If one were to ask what martial arts the Divine Maiden Sect used, very few people would know.

Even in the present, the Divine Maiden Sect was not quite considered a recognized martial arts sect.

The one being recognized was Ximen Surin as an individual, not the Divine Maiden Sect.

But once another peerless master emerges after the Zenith Among Women, the situation will change.

Reputation meant a continuing force. As such, people would think there must be something to the Divine Maiden Sect, thus acknowledging the birth of a new prestigious sect.

"So, I hope my disciple can help me out. If you really do not wish to, I cannot force you."

"Help you? It is my duty to do so. Of course, I will simply do as I'm told."

Qing immediately changed her mind.

Anyway, if I'm going around looking at sword walls and traveling through Jianghu, who's going to find me and make me work?

Ximen Surin did not even try to hide her pleased expression. How could such a kind, gentle, and obedient disciple just fall into her lap? It seemed like all the good fortune of her three lifetimes had gathered in her old age.

Recently, she had been diligently meeting with old acquaintances from the Orthodox Faction. And she just loved seeing how envious they were of her.

Qing didn't mind it too much, though she did feel a bit awkward.

So she added,

"Besides, as Master said, unless there is a great upheaval in Wulin, there won't be any forced summons, right?"

That was what Qing said.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

If the Orthodox Faction of Wulin had the Murim Alliance, the Unorthodox Faction also had their own coalition.

It was called the Under Heaven Martial Union of Unorthodox Heroes!

Or the Unorthodox Union for short.

It was a very grand name, but the Unorthodox Faction had a tendency to be very particular about appearances.

The martial artists of the Orthodox Faction called them bastards of the Unorthodox Union, saying they were Unorthodox, not heroes. They also made it easier to pronounce the last syllable.

Anyway, the current Union Lord of the Unorthodox Union was someone called Bu Anpyeong. His title was Warlord and he was known to be the third-ranked among the Ten Great Masters Under Heaven.

However, Bu Anpyeong did not acknowledge this.

Because, in his mind, he had always been the Greatest Under Heaven.

Unlike the Orthodox Faction, in the Unorthodox Faction, one had to thoroughly hide their true abilities.

This was because backstabbing at any opportunity was considered a virtue among the Unorthodox Faction.

If news spread that someone had been betrayed and killed, people would actually curse at the betrayed, calling them a retard for upholding the law of trust and sincerity.

In such a ruthless world, revealing one's full strength was an invitation to get stabbed in the back.

Thus, when rumors began to spread that Great Master Bu had reached the Mid-Stage of the Mysterious Heaven Realm, he had already entered the Late-Stage.

Of course, the extent might differ, but hiding one's abilities was just as common in the Orthodox Faction. If the Orthodox Faction hid about ten percent of their abilities, the Unorthodox Faction had to hide about fifty percent.

So, when news came that the Great Master had broken through the Mid-Stage of the Mysterious Heaven Realm, it was safe to assume he was already looking beyond the next realm.

Anyway, these days, Warlord Bu Anpyeong was thoroughly enjoying himself.

After all, good news kept pouring in every day.

"Union Lord."

"Oh, what is it? Did another place fall?"

"It's the Dragon Gate Sword School and Yeongdeok Gate, Branch of the Union Lord."

"Kekeke, they say not to kick a man when he's down, but aren't those Blood Cult bastards surprisingly helpful?"

"But, is this really alright? They are still the Blood Cult, after all."

"Well, do we have any dealings with the Blood Cult? Did we collude with them?"

"A dog starved of food will- Argh!!!"

With a soft thud, the subordinate who had been reporting suddenly rolled on the ground, screaming.

"I told you not to use proverbs. If you want to speak, just speak plainly. Why do you have to show off that you're literate? Who doesn't know how to read?"

Bu Anpyeong came from a family of Confucian scholars, as evident from his well-established name.

It was a story of how a man from such a family of integrity became the leader of a gang. It was a long and winding tale…… or not.

He was just a guy who, despite having exceptional martial talent, held a deep grudge against the world due to continuously failing to obtain an official position because of his humble family background.

If he had managed to enter the Imperial Palace early on, he might have become a Celestial Martial Emperor from the Imperial Palace. Or perhaps a Celestial Martial Grand General from the Imperial Palace. He would have been a superhuman, complete with a scholar's integrity, academic knowledge, and a martial artist's martial prowess.

However, even if someone in the Imperial Palace knew this and experienced the miracle of traveling back in time, there would have been no way to break through the holy trinity of blood ties, regional ties, and school ties. As such, he had absolutely no connection with an official position from the start.

(The opinions of the strategy writers may differ slightly.)

"Haaak, it was too powerful an attack. The Union Lord's greatness grows more and more each day!"

Bu Anpyeong had just flicked his finger with Qi, so the subordinate rolling on the ground was just expressing his flattery by throwing himself around.

"You brat. That's why I can't bring myself to hate you. So, what's this about a dog starved of food?"

"A dog starved of food will bite its owner. Basically, it means the weak may turn against the strong."

"Ha. That's something we don't say. That's something those Wulin Alliance bastards would say. Anyway, if the Blood Cult reveals their true colors, we would be in a position to ask them for help. So what if we're a bit stubborn and annoying now? Would they stab us first, saying we should die together?"

In fact, if the Blood Cult showed up, the Unorthodox Faction would just have to protect their own territories and lie low.

However, the Wulin Alliance, which had the justification of protecting the peace of Zhongyuan, could never just stay put and protect their own territories.

"So tell our family to keep the party going. Tell them to gather everything that the Blood Cult has swept through. At this rate, Yangzhou and Jiaozhou will be under the control of our Unorthodox Union."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While chaos reigned in one part of Zhongyuan, communication in the vast land relied entirely on manpower, which was primitive to say the least.

It was still far from being known.

Just look at what happened during the incident on the Yangtze River.

It took a month for a complaint to reach the Wulin Alliance regarding Un Yeonyoung after the Demonic Cannibal's death, another month for an investigation team to be dispatched, another month to return and organize, another month to reach the Un Clan, and another month to investigate and produce results.

It took five months, even with the urgent mobilization of manpower.

So, the unsettling events taking place in that remote corner of Zhongyuan were still a long way from being known.

It would only be known after the Wulin Competition ended and people slowly returned home, only to find their homes in ashes and then go back to the Murim Alliance to ask for help.

Thus, the atmosphere in Kaifeng, with only the closing ceremony of the Wulin Competition remaining, was lively with the lingering excitement of the festival.

And there was one person who was particularly lively.

"Hmm. The restaurant seems a bit dark, don't you think?"

Peng Daesan gritted his teeth.

"Can't you please stop it already?"

"Alright, alright. I'll turn on the lights for you. Look. Ta-da."

Qing infused Qi into her Blue Porcelain Sword.

The biggest difference between Sword Qi and Sword Force was whether it emitted light.

In fact, to ordinary people, both were sharp, and their names, Sword Qi and Sword Force, were similar.

But Sword Qi only glimmered faintly like a glow-in-the-dark object, whereas Sword Force provided a faint light source like starlight.

But starlight was still starlight, even at night. What use would a single ray of starlight be in broad daylight?

It was just that the Blue Porcelain Sword evolved, or rather, powered up into a very, very shiny Blue Porcelain Sword.

"Plus One Blue Porcelain Sword. Ah, so bright. It's no good to have a gloomy atmosphere when eating. With just Sword Force, you don't even need a lamp. It's reassuring to have this even on a dark night."

"I've never heard of anyone using Sword Force as a torch in my entire life."

"What are you talking about? If some weirdo attacks you in the middle of the night, you can just use this to finish them off. Sword Force can cut through weapons, you know? Those who only use Sword Qi probably don't know, but…"

"Urgh."

"Kuk."

Peng Daesan and Namgung Shinjae both groaned simultaneously. Qing's expression became even more triumphant.

"Especially Sword Acquaintance should try harder. At this rate, you'll be called a Sword Disciple or a Sword Servant instead of a Sword Acquaintance. You should quickly become a Transcendent Sword, instead of just a Peak Sword."

"……Let's just call ourselves Sword Friends."

Namgung Shinjae, who had brought up the term Sword Acquaintance, ended up taking the brunt of the humiliation.

Originally, Namgung Shinjae had made a pointless vow to reach the pinnacle with only swordsmanship, even though no one had asked him to. It was also a source of concern for the head of the Namgung family.

However, at this very moment, he was genuinely thinking that the world was a very dirty and nasty place, and that he should quickly elevate his realm, regardless of whether it was through the sword or not.