\chapter{Transcendent Qing(3)}

As Qing entered the room, the guest who had been sitting jumped up
abruptly, fidgeting and wringing their hands together, their eyes darting
around nervously.

They were unable to speak, their lips merely moving without a sound.

"Goodness, Young Lady Moyong. You look so haggard. What's the use of
having such a pretty face if you're going to use it so roughly?"

Her face looked gaunt, as if she hadn't eaten in days.

Her cheeks were hollow and dark circles had formed under her eyes, so
much so that it seemed they would soon reach her cheeks. Her lips were also chapped and her skin had a rough texture to it.

Moyong Juhui hesitantly opened her mouth.

"Hello……. Have you been well……?"

"I have been well, but it does not seem like Young Lady Moyong has been.
Is something the matter?"

"Well, that is……"

Then, she went back to the start, completely shrinking and stammering
without being able to continue.

Qing wondered what to do, before deciding to just sit and wait for
Moyong Juhui to speak.

After about an incense's worth of time had passed…

Qing was just thinking of new retorts to say to vex her to the
Transcendent Realm.

"Um, you see. I was wondering if you could do that thing just once……"

"What thing?"

"That, you know. That you're going to be okay. That everything will be
alright, and that it's not my fault……"

At that, Qing let out a deep sigh.

What in the world did she do after going home for her condition to
worsen so much? Even when she was here, she wasn't like this. 

To be fair, Sir Moyong seemed like a good person.

At Qing's sigh, Moyong Juhui flinched, no, she practically jumped, her
shoulders shaking.

Then, she hung her head low.

At that, Qing let out another deep sigh.

I can't even sigh in front of a sick person, huh?

But to be honest, it wasn't like she particularly held back on sighing
either.

"Young Lady Moyong? Come here."

"Yes……"

As Moyong Juhui hesitantly inched closer, Qing patted her thigh.

It was a gesture anyone could understand.

"Th-That……"

"Come on. Hurry."

At that, Moyong Juhui awkwardly settled on Qing's lap. She was so stiff
that it was hard to tell whether she was a person or a wooden block.
Qing then embraced Moyong Juhui and whispered in her ear.

"I hope Young Lady Moyong does not hurt too much. After all, it is not
your fault. The Blood Cult bastards are the bad ones, so why should you
be hurting? It will be okay. It will get better. And it will be even better in
the future."

Then, a subtle tremor spread through her. At the same time, she felt a
muffled sob.

Ah shit, why is she crying so pitifully?

Can't you just ask first like, 'Can I cry?' before going, 'WAAAAAAAH!
WAAAAAAAAH! WAAAAAAAAAAAAAH!'?

Should I tell her to cry even more, so she can feel better?

If you cry, your purity, no, that's not it. Where did I hear that? Anyway.

Qing pondered for a moment, before deciding to just stay still. She was
worried that if she told her to relax and feel free to cry, she would try to
hold it in, thinking she was being a bother.

Is this correct? Dear psychology lecturer whose name I can't
remember, no, never even remembered in the first place?

If a psychology lecturer from beyond time and space heard this, they
might have answered.

Reckless physical contact with a client, D. Don't even think about
retaking the course. Let us never see each other again.

In truth, Qing thought that a hug was a cure-all, believing that it would
calm an anxious person's mind, heal their wounded heart, and since the
body and mind were one, the body would also heal naturally on its own.

It was a posthumous judgment learned from her experience of being
comforted by Gyeon Pohui.

After a long while, even though a body as superhuman as that of
hardened steel felt no discomfort from having Moyong Juhui on her
lap, Moyong Juhui seemed to have calmed down, her voice still thick
with suppressed emotion.

"I, I am okay now."

"I'm okay too, so just stay like that. But what happened? You don't have
to tell me if you don't want to, but wouldn't it be a bit more comforting
after talking about it?"

"That is. Actually."

Moyong Juhui confessed what her father had said.

Aigo, that old man. I didn't think much of him, but it seems he has
some pretty radical ideas.

"If it's that difficult, why didn't you just tell him everything? Like, 'I'm
hurting, so why are you saying such things?' Why, I know you're good at
that, Young Lady Moyong."

"If, if Father hadn't said that, I would have told him, but after hearing
those words, I couldn't. He would be hurting twice as much……"

"My, how thoughtful of you."

As Qing was thinking that…

Didn't he say she was hurting because of me? Wasn't I the one who
saved her?

Now that I think about it, isn't that a bit unfair?

Moyong Juhui couldn't see Qing's face since she was being held from
behind.

If she had, she would have seen the ominous colors dawning in the
center of her eyes, the space that was supposed to be pitch-black.
Qing was now Transcendent.

The Transcendent Realm allowed one to wield Sword Force.

Sword Force was the release of the starlight inherent within a martial
artist and the star Qing was born with was the Heavenly Slaughtering
Star, the most dreadful star among the Three Thousand Worlds.

It was different from the Heaven-Shattering Demonic Qi that laughed
to itself with a pathetic 'Kekeke' while being beaten up by Qing every
now and then in the dantian.

It was an ominous light that lingered leisurely in the deepest trench of
hell, even among the Six Paths of Desire. As such, it knew that a mere
human could not overcome the will of destiny.

So, the lonely star of Heavenly Slaughter merely played along with its
avatar, as if watching a child's antics.

Whenever she resisted with the knowledge of Daoism and Buddhism, it
retreated as if it couldn't help it.

"But why did you hurt my chest so much? You even used your Inner Qi
that time, didn't you? If I were an ordinary person, it would have been
completely crushed."

A chilling voice.

Moyong Juhui's heart sank.

"I-I'm sorry, I was a bit out of it at that time, I won't do it again."

"It's not a matter of being at fault. Why did you do that? Was I someone
who could be hurt, for Young Lady Moyong?"

"N-No, that's not it. It's just that back then, I kept recalling painful
memories when I saw you, Young Lady Ximen, so I was a bit out of it.
I'm sorry."

"Huuueum."

What to do? It was a coquettish hum.

Moyong Juhui froze like a wooden block.

"If it's just an apology, how can I trust Young Lady Moyong's sincerity?"

"Th-Then, my fingernail, I'll let you pull out my fingernails. Since you
like that."

"Your fingers are pretty, so it's a waste to pull out the fingernails, isn't
it? They say it's an eye for an eye, a tooth for a tooth."

Qing's hand, which was holding her tightly from behind, slid under
Moyong Juhui's jacket. The icy cold hand crept up like a snake, slowly
heading towards her chest.

And then, a soft chuckle.

"My goodness. There has to be something to squeeze for us to do the
same. But like this."

"I-I'm sorry for being small."

"You should speak properly. It's not that you're small, but rather,
shouldn't we say that you have nothing in this situation? Woah, what's
this? My goodness. What is this doing here. Should I just twist this off?
Here, it's going to sting."

"Huek."

Sting. Moyong Juhui let out a gasp.

It was a strange occurrence. Normally, this was her most sensitive spot
that made her hate to be touched, but at this moment, it didn't, and it
hurt. It should hurt. A lot. Very much so. Her heart was pounding like
crazy with fear, so why? But, but…

"I-If you wish, if Young Lady Ximen wants to do that, as much as I
did……"

Moyong Juhui's response trembled.

At that, Qing blew into her ear.

Moyong Juhui, who was sitting on Qing's lap, bounced up, but was held
back by Qing's firm arms.

"My. It was a joke. Young Lady Moyong was not in her right mind back
then. I understand that much. So, are you still hurting when you see
me?"

"N-No. That wasn't it. I kept recalling memories, but I felt relieved
seeing you, Young Lady Ximen. I wanted to hear your voice……"

"Is that so? Ah. That's right. Since Young Lady Moyong is being honest
for once, should I ask everything I'm curious about? Why did you
follow me all the way to the training grounds and sit there like a pitiful
person? You were so pitiful that I couldn't help but notice you."

"I-I couldn't sleep at night. I get scared when there's no sign of people,
so I can't sleep. I'm scared that when I open my eyes, I might be in a
box, or captured again. So, so, the place that felt safest was there."

"Ah."

Hearing words that were not so different from her own, Qing felt a
surge of empathy and her mind cleared.

Qing also couldn't sleep alone due to the same fear.

She was close by, sharing the same symptom of insomnia, but she hadn't
noticed.

"No, well, you should have told me. If you don't say anything, how am I
supposed to know? How tough insomnia can be. Aigo, you must have
suffered. I was inconsiderate. I'm sorry."

"N-No, no. Why are you sorry? I, I was just being really mean. I'm
sorry, I'm sorry."

In any case, unlike before, when her speech was a mix of formal and
informal language and her gaze shifted between friendly and abruptly
distant, her current state was completely different.

As she sat on her lap, still restless and stiff, her voice was more polite
than ever, truly conveying her sincere apologies.

It seemed like Qing's mental therapy had been sufficiently effective.

It also didn't seem like she would target her chest again.
Qing decided to be generous.

"If it's too difficult, you can stay at Mucheongak. Well, I have to go back
after the Wulin Tournament's closing ceremony, so it's only for a few
days."

"Can I really do that?"

"If that's what Young Lady Moyong wants."

However, Moyong Juhui shook her head.

Although, from Qing's perspective, it was just the back of her head
shaking right in front of her nose.

"No. If I do that… I think I will remain weak and pathetic like this forever.
Time will pass, and one day, I will be able to forget everything and be
okay, right?"

It was a surprisingly admirable statement.

Qing's expression also softened in satisfaction.

Perhaps this could lead to the propagation of psychiatry in the Central
Plains.

Later, I should tell Nanah about this, so she can develop it further
with the Tang Clan.

At any rate, thinking it was a good thing, Qing answered with sincerity.

"Of course, you will."

And then, the atmosphere became a bit ambiguous.

It felt like the conversation had reached its conclusion, but Moyong
Juhui leaned comfortably on her instead.

What's going on? Isn't she about to leave? Why is she leaning on
me?

Should I keep hugging her like this? I think she's calmed down now, so
shouldn't I let her go?

But isn't it customary to ask if it's okay to let go in this kind of
atmosphere?

Why is she just staying still?

While she was thinking that, Moyong Juhui cautiously spoke up.

"Um, by the way."

"Yes."

"I think I made a big mistake towards you, Young Lady Ximen. I don't
think I can be comfortable like this, so, since you said it's an eye for an
eye, a tooth for a tooth, if you continue what you were doing earlier……"

"Ehhh, I said it was a joke. Then what am I supposed to do? I can't be
joking, can I?"

"But that way, I think I will feel a bit more at ease, so can't you?"

"Just let it go. You weren't in your right mind back then."

"But, I will keep being bothered by it……"

Despite Qing saying it was okay, she was quite persistent in her
request.

Moreover, since she said it would make her feel more at ease, Qing
wondered if she should comply for the sake of her mental healing.

"If you really need to be punished to feel at ease… Will you stand up for
a moment? And also, close your eyes tightly."

At that, Moyong Juhui swallowed hard.

And then, she obediently stood up and tightly closed her eyes-
Qing sighed deeply.

I feel like I shouldn't be doing this, but what can I do when she says
she needs to be hurt to feel at ease?

It seems like this is the moment for the first ever nuclear launch after
reaching the Transcendent Realm, she thought.

Thus, above the tightly closed eyes of Moyong Juhui, Ximen Surin's
style of nuclear fusion ballistic knuckle bomb, the ultimate technique,
'Solemn Punishment', descended.

SMACK!!!