\chapter{Transcendent Qing(6)}

Sima Chunbong reminisced about a satisfying conversation with a
companion of the mortal realm, or perhaps with a worthy rival in a
battle of pride among geniuses.

"Yes. We should definitely compare and see who is better."

First, the appearance.

Mm. There are many forms of beauty. As such, it is impossible to
determine the superiority between a glamorous yet refreshingly
arrogant beauty and this beauty here, who is akin to a well-forged
sword.

So, it's a tie. A tie!

But the Celestial Blossom Sword is too tall for a woman, so this lady
here, who is just the right height, wins.

As for the chest, this lady here has a bigger one, but, mm, in terms of
talent, this lady wins.

In terms of achievements, there's the subjugation of the Blood Cult,
victory in the Hidden Dragon Martial Competition, and the
enlightenment of a poor beast. But this, too, is a win for this lady here,
who has comforted the common people by handling numerous tasks as
the Vice-Commander of the Wulin Alliance.

And in terms of brilliance of mind, this lady wins as well.

Of course, as a martial artist, her realm is a defeat.

However, as someone who is destined to become a commander, this
lady, who commands all, is far greater than just a single individual's
martial prowess.

"Hehe, this lady's overwhelming victory, it is. Celestial Blossom
Sword, you must try harder if you wish to stand shoulder to shoulder
with this lady."

Compared to the genius and perfection of this Sima scion, there are
some shortcomings. Still, unlike the utterly incompetent fools, this
lady is worthy of her companionship.

It was a very satisfying conclusion.

If Qing had heard this, she would have been so dumbfounded that she
would have launched a Ximen Surin-style nuclear bombardment. After
all, someone who didn't need to use their brain because of their
outstanding martial prowess had said these things.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Is that what you're supposed to say to me right now? You brought
another woman and said let's sleep together, so confidently."

"I'm sorry. But look at Young Lady Moyong's condition. It's a mess. She
can't even sleep at night. You've seen it yourself, you know? How she
was dozing off miserably in the training grounds. She says she feels at
ease when she hears my voice, so she was dozing off like that."

Tang Nanah was one of the few people who knew about Moyong
Juhee's kidnapping.

"Hmph. It can't be helped. Qing'er is just too kind for her own good.
Giving in to such an obvious trick."

It was the all-too-kind Qing (hobby: dismantling living villains). Since
she was willing to take care of a mentally ill child, Tang Nanah, whose
fundamental nature was that of a physician, could only say, 'Well, what
can I do?'.

"I'm telling you in advance. I hate you. But I'm going to sleep with you
both to keep an eye on you, in case you do anything to hurt Qing'er
again. Don't even think about considering me a friend or anything like
that."

That was how Tang Nanah growled at her.

However, Moyong Juhee wasn't one to just listen quietly, either.

"Ha. As if. As if someone like you could say that to me. You crazy bitch
who releases poison without a word of apology. Who in the world
would want to be friends with a bitch like you?"

"Sigh. Young Lady Moyong. No bad words."

"But she, she was the one who started it."

"If Nanah dies, will you die too, Young Lady Moyong? Are you going to
act childishly like a baby?"

It was almost like she was treating her like a child. No, she was
outright treating her like a child.

However, Moyong Juhee had been acting almost like a child, so one
could say that the situation was fitting. Moyong Juhee pouted,
expressing her resentment.

"But, but……!"

"Sigh. You're going to get scolded. And Nanah didn't use bad words, did
she? Apologize to Nanah."

"I-It's just, that, uh, Young Lady Tang, I'm, I'm sor……"

Moyong Juhee's lips trembled, unable to speak properly, before she
eventually shouted.

"You crazy bitch! You were the one in the wrong first, ah, heuk."

In the end, after being severely pinched, Moyong Juhee offered an
apology.

The expression of Tang Nanah, who was receiving the apology, was
bitter.

"What, what is this? It's, it's a bit strange. Why do I feel?"

"She apologized. Just accept it."

"No, she's a bit strange, isn't she? Why does she have such a satisfied
look on her face?"

"She's just relieved because she apologized first. Young Lady Moyong,
you did very well. But shouldn't you listen to me before getting
punished?"

"I-It's just, um. The inner part of my arm seems to have adjusted a bit.
Somewhere else, a different place……!"

"See, I told you she's a bit strange."

"She's just in pain. It'll get better. Right, Young Lady Moyong?"

"Yes. Thanks to you. I'm always grateful."

Tang Nanah's eyes narrowed, unable to look away. But there wasn't
much Tang Nanah could do about it either.

In any case, Moyong Juhee would lie down with Qing in front and Tang
Nanah behind her. Then, after no more than four breaths, she would
fall into a deep slumber.

Even Qing, who could fall asleep within a minute of lying down
anywhere, couldn't fall asleep within four breaths.

As such, one could only feel pity for Moyong Juhee, wondering just
how tired she must be to fall into such a deep sleep.

Because of that, Qing grumbled at Tang Nanah.

"See? How could she sleep like this if she wasn't so tired? Why do you
keep saying she's strange when she's in pain? Sure, she's a bit of a
spoiled brat, but be nice to her. Memories from when you're sick last
the longest, you know?"

"Sigh. I wonder if she's really suffering from a lot of mental trauma.
And here I thought she had some other motive. What could I have
known……"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since the newly-constructed Great Assembly Hall was located in a
corner of Kaifeng, it was quite a distance from the Wulin Alliance. It
was because someone had thoroughly messed up the Water Arena.

And that someone was on her way to the closing ceremony.

Qing tilted her head.

"What is it? Why are there so many women in veils all of a sudden?"

Indeed, it was as she said. For some reason, there were many women
wearing veils.

Since Peng Daesan was among the group, the density of women was
so high that it formed a wall, pushing them towards the closing
ceremony.

So, looking around from the center, about one in five women wore a
veil.

Qing shrugged.

"I guess I've started a trend in Zhongyuan. I mean, it was bound
to happen. The Transcendent Realm's Super Ultra Qing. Who wouldn't
want to imitate me?"

"Ha. What a joke. Aren't you overestimating yourself?"

"Why? What. Did I say something wrong? Aren't they imitating me?"

"They may be imitating you, but in the end, it's just a ploy to look good
for me."

"Ehhh. Sanie is overestimating himself, too. Do you think all the women
in the world are trying to look good for you? Um. It seems like they are
trying to look good for you, though."

Qing, who had been poking Peng Daesan's side with her elbow, changed
her words at the sight of the veils' brims all turning towards them at
once.

It was a desperate love that could even pierce through veils.
Qing's brazen actions were met with intense gazes that could pierce
through the veils.

"A-Are there no rumors? Why are these women still chasing after you
like this, forming walls?"

"W-Well, there are rumors. T-That a woman with a large chest and
buttocks would make that bastard go crazy for her, even if she was
dressed like a beggar. I heard it from the members of our
Participation Society."

Moyong Juhee informed them in a small voice.

The members of the Yongbong Assembly's little group, which was led by
Moyong Juhee, had come to visit her in concern. And one out of three
stories they told was about Jade Qilin, saying that the preferences of
the Most Handsome Man Under the Heavens these days were quite
unusual.

"So that's what they say?"

"Since nothing has changed, I thought the rumors hadn't spread.
Fortunately, they did. But why are they still like this?"

Peng Daesan spoke as if he couldn't believe it.

Qing was also dumbfounded.

So the rumor that he had been with a beggar had spread, but they're
still here. Ah. So now they're dressed as beggars and even wearing
veils.

To think they would mass-produce beggar cosplayers……

They were almost like the most devoted members of the Half-Sword
Duo Association, weren't they? It seems that the Most Handsome Man
Under the Heavens' troubles were still ongoing, so they came to
seek refuge, huh?

"Hey, San. By any chance."

"What is it?"

"Have you ever considered spreading a rumor that you like women who
completely expose their chests?"

"Why?"

"Wouldn't it be interesting to see how far they'll follow? Also, I'm full of
personal interests. It's nice to look at, you know? If it's the same
scenery anyway, it's better if there's a lot of skin showing."

"Hm. It wouldn't be bad to be treated like the greatest pervert under
the heavens if it means they'll fall off. But how do you plan to spread
such a rumor? Are you going to walk around with your chest exposed in
front of others, just like you said?"

Peng Daesan trailed off.

Then, his complexion became stiff. Qing read that expression.

What? Why? Why are you getting upset?

Regardless, it was a statement that should not be taken lightly.

"Not me. Look over there. Oh, do you see that lady with the exposed
cleavage? The one in blue clothes with a red sash. Wow. If she just
jumps a bit, everything will spill out. Now, just stare at her
intently."

"What?"

"If you just keep looking at women with the most exposed skin, people
will notice and say, 'Oh my, Young Master Peng is looking at her
breasts. He's looking at them so openly'. Then, they'll all start imitating
her."

It was Qing, whose brain worked exceptionally well when it came to
scheming against others.

"Hm. That's not a bad idea."

Peng Daesan was genuinely curious about how far these women would
go.

Already, one in five were dressed as beggars and one in four were
wearing veils. Moreover, there were women with unnaturally large
chests and buttocks, though if they wanted to put something in there,
they should at least try to make it look natural.

So, as a man and a woman stared explicitly at women with exposed
cleavage, heading towards the closing ceremony, the women, who had
been observing Peng Daesan's beauty, could not help but disperse with
a sense of regret.

The members of the Half-Sword Duo Association were originally the
future leaders of the Orthodox Faction, the ruling class.

And the ruling class did not mingle with the ruled class.

They mingled among themselves on a special platform above the
ladder, looking down at the crowd below.

Thus, as soon as they sat down on the special seats, they thought that
they would be bored even before it began, wondering when this would
all end.

After all, they already knew what the major announcement would be at
the closing ceremony.

First, there would be the news of the subjugation of the Blood Cult.

"……And so, through a covert operation, we have eradicated the evil
scions of the Blood Cult! I am pleased to inform our comrades of
Jianghu of this with a joyful heart!"

"Wooooooooah!!"

"The Wulin Alliance is the best!"

It was met with enthusiastic cheers and support.

And then, there would be an announcement that they would also take
care of the black dens.

But it was not to help the Demonic Cult, nor was it to imitate them.

Absolutely not.

It was a clarification, not an excuse, that they had only delayed this
due to the covert operation to capture the Blood Cult. They had never
intended to idly stand by and watch the evil gangs that harmed the
world.

After this announcement, quite a few people turned pale and hurriedly
left.

This was the very definition of the chivalry of the Orthodox Faction of
Wulin.

Half of those involved in the black market were martial artists and the
other half were ordinary people.

They would give a warning before taking action.

We're really going to fuck you up, so run away if you want to.

After that, there was an announcement of a new member of the Ten
Noble Clans to fill the vacancy of the Jinju Un Clan.

"In the past, we have suffered the sorrow of losing one of the great
pillars of the Orthodox Faction of Wulin. However, we cannot make
the mistake of neglecting to reinforce the house just because we have
lost a pillar. Thus, I would like to introduce a new pillar to you, our
comrades of Jianghu."

Qing looked at Gongson Yoyeo and her family, who were on the
podium.

The new Ten Noble Clans was the Gongson Gong Clan.

According to Sima Chunbong's argument, it was originally the
disposition of the Sima Clan to not step forward or something.

There was no persuasiveness in the words of someone who had fallen,
so, well, it must be what it is.

If it wasn't for Gongson Yoyeo, she wouldn't have come to this place.

Even if it was a major announcement, the prominent figures of the
Nine Sects One Union and the Ten Noble Clans, as well as other
prominent Masters, had already heard about it or participated in the
decision-making process.

Therefore, there weren't many high-ranking individuals who actually
attended the closing ceremony.

It was just a formality, with people in ambiguous positions, who were
high-ranking enough yet could be easily replaced, watching with bored
expressions.

Ximen Surin had already left, saying she had been away from the sect
for too long. It seemed like she left with a light heart, having shown off
everything she wanted to and receiving all the envy she could for her
talented disciple. To Qing, it felt like she never knew Ximen Surin could
smile like that.

The reason Qing didn't leave with her was because of the order to visit
the Shaolin Temple with the bald monks, see the Absolute Sword Wall,
and then take a tour around as much as possible before returning.

And since her friend's family had a celebration, she had to congratulate
them, of course.

Qing clapped hard and cheered loudly.

Gongson Yoyeo seemed to scan the VIP seats and made eye contact
with Qing.

Then, the woman smiled brightly, her white teeth sparkling……

It was the end of June. It was summer. 