\chapter{Transcendent Qing(5)}

Sima Chunbong tried to maintain her composure.

After all, a poker face was an essential quality for a genius.

Of course, only she herself thought that her expression was perfectly
controlled.

From Qing's perspective, it was just Sima Chunbong's already fierce
countenance becoming even fiercer.

So, she thought to herself, 'Wow, her glare is a bit intimidating, but did I
do something wrong?' and tried to recall what she had done.

Perhaps I was too late in repeating her title?

But the answer was something else entirely.

"That woman hates being called Zhinan Xianhua. She said she hates
having those ridiculously large, vulgar lumps of flesh, which she
desperately tries to hide, being referred to as Wisdom Pouches."

Moyong Juhee tattled on her.

"Sigh. You shouldn't use such vulgar words. Use elegant words instead.
You promised to become a better person, didn't you?"

Come to think of it, I feel like I've said something like this before. Ah. It
was to the little kid Moyong.

To think they're siblings, they're so alike.

And it seemed she was just as obedient, as she replied meekly.

"Ugh. Yes. I will, I will try to."

"Good girl."

Qing patted Moyong Juhee's head.

Meanwhile, Qing couldn't see Moyong Juhee's expression. She had
placed her on her lap and rested her chin on her shoulder, so she was
looking at Sima Chunbong, who had shown up uninvited.

However, from Sima Chunbong's perspective, she could see Moyong
Juhee's expression becoming more relaxed the moment her head was
patted.

Seeing that, Jinang Hyeonhwa exclaimed in admiration.

"Oh my, how in the world did you tame that wild beast? Even when this
one explained the principles and logic, that beast wouldn't listen. But
how did you make her so docile, like a tamed animal……!"

It was safe to say that not thinking with just one's head was one of
Jinang Hyeonhwa's many talents.

Whether it was a beast or a livestock, both were not considered human,
which was a testament to Jinang Hyeonhwa's brilliant intellect.

"What?! Beast? Livestock? This pig with swollen tits… …!"

"Sigh. Foul language."

"But she, she started it first."

"Does it matter who started it? Do you have to stoop to the same level?
Didn't you promise to become a better person? And what do you mean
by she started it first? Is Young Lady Moyong some seven-year-old
kid? Is that something a grown woman should say?"

"Ye, yesss. I'm, I'm sorry."

Moyong Juhee's resentful and childish protest was met with Qing's
melodious voice whispering in her ear, making her lose focus and
respond without even knowing what she was saying.

It was thanks to this that Moyong Juhee suddenly recalled something
later on.

'Didn't she say that we should just return tit for tat, an eye for an eye, a
tooth for a tooth? Back in the underground, she said to return the pain
in kind… Ah, ahh……'

As Moyong Juhee was on the verge of realizing Qing's double standards,
she suddenly remembered the time when she was dismembered,
covered in fresh blood. Her eyes unfocused and she went blank.

However, Qing couldn't see her, and Sima Chunbong wasn't particularly
interested.

Instead, her interest was elsewhere.

"How, how did you tame this beast-like, no, even beasts know to be
cautious and reserved in front of a life form superior to them, so this
thing that is less than a beast, this savage, um, livestock, no, that's not
it, yes, how did you tame this, this something that is less than a beast?"

"That expression of taming is a bit……."

"Then, how did you make this foolish woman so docile?"

"Aren't those practically the same thing?"

While saying so, Qing didn't particularly deny the phrases 'less than a
beast' or 'foolish'.

"Hmm. Wait. Different expressions, huh. This is interesting."

Sima Chunbong struck a pose that clearly shouted, 'I'm thinking' to
anyone who saw. It was a pose where she crossed her arms and stroked
her chin with her right hand.

"Yes. Enlightenment! How did you enlighten this foolish and savage
woman? Or should I say, reform?"

"Uh…… Faith, love, and patience?"

"Indeed! Excellent! I can believe that. It seems you are truly a genius,
Young Lady. I can see the value in sparing the most precious and
expensive time of this one."

Qing had seen many strange people in Zhongyuan, but this
person was exceptionally unique among them.

If one were to describe a unique person in a way that made them sound
impressive, one would call them a prodigy.

"Uh, may I ask why you are here……?"

"I came to see what kind of person you were, to see with my own eyes
whether you were a rare talent, as the rumors said. And I also had
something I wanted to ask if the rumors were true. Indeed, you seem
qualified enough to hear this one's question."

She was a strange person, but at least she kept complimenting her.

So, what's the issue? She's a good person.

"About that. What is it that you wish to ask?"

Suddenly, Sima Chunbong, who had been acting so full of herself,
shrank back and asked in a hushed voice.

"How does the Celestial Blossom Sword walk around with those
shameful lumps of flesh so exposed?"

"……? What do you mean by shameful lumps of flesh?"

"Those parts of a woman's body that are merely organs for producing
milk to feed children, yet vary in size from person to person, thus
becoming an unfair standard of evaluation."

In short, Qing summarized the long-winded explanation.

"You mean breasts?"

"Yes. How can the Celestial Blossom Sword walk around with those
shameful lumps of flesh so exposed?"

"Me? When did I? I've never exposed them except when I sleep."

"Oh, come now, why are you suddenly acting like a dull commoner?
Not exposed as in naked, but their size is fully visible. She even wraps
her waist with a sash, making it so that the whole world knows the size
of the Celestial Blossom Sword."

At that, a sound of grinding teeth and a resentful, seething mutter was
heard nearby.

Should she just ignore it as if she were talking to herself? Since it was
still a conversation, Qing decided to let it go.

"I'm not trying to emphasize the size. If I don't use a sash, my posture
looks dull, you see?"

"Then, wouldn't it be better to hide it like this one does? Haven't you
heard the foolish commoners whispering? Why should one be known as
just a woman with big breasts when that is not reflective of who she is?
This one's actions and achievements are not considered, only that her
breasts are big."

This was why Sima Chunbong concealed her breasts. As the youngest
Deputy Military Advisor and the future youngest Supreme Military
Advisor of the Wulin Alliance, the genius who would become the
practical leader of the Orthodox faction did not want to be known as
just a woman with vulgar breasts.

It had been years since Sima Chunbong started binding her breasts, yet
the ridicule of being called Wisdom Pouch and Three Perfections had
not subsided.

Thus, she had no choice but to absolutely loathe such a thing.

In fact, due to the general perception in Zhongyuan, women with
large breasts were considered vulgar, foolish, and promiscuous.

Even if one were to take a mistress, one would never take such a
woman as their wife because it was shameful and lowered their status.

It was unimaginable to present such a woman in front of others as
one's wife.

While it was considered impolite to call an ugly woman ugly to her face,
it was fine to insult a large-breasted woman by calling her vulgar.

At that, Qing replied.

"Eh, who cares what others say? I'm fine as long as I'm confident. And
if you're known for something other than your breasts, then that's fine,
isn't it? Instead of being known as just a woman with big breasts, you
can be known as a woman who also has big breasts."

At those words, lightning struck in Sima Chunbong's mind.

"A woman who also has big breasts……"

The first part was something Sima Chunbong also thought. 'I should
just ignore the foolish and ignorant masses. My value does not lie in my
breasts', she had thought.

But to be a woman who also has big breasts was a truly innovative idea!

"Wait, wait a moment, if you would."

After saying so, Sima Chunbong staggered away.

At that, Qing tilted her head.

What's wrong with her? Anyway, more importantly…

"Young Lady Moyong? You're going to ruin your teeth. You should
cherish what teeth you have left, especially since you're missing four
compared to others."

"B-But, that bitch is saying such infuriating things. That evil, pig bitch……."

Grind, grind. The sound of teeth grinding was quite loud once again.

Qing sighed deeply.

At that, Moyong Juhee shuddered.

"You promised not to use such wicked words."

"I'm, I'm sorry. Then, should I, should I get punished? If I get punished,
I think I can fix it………"

"Why, do you want to get hit on the head with my knuckles some more?
If you keep doing that, your head will be as tall as a mountain. What
should I do about that?"

"N-No knuckles!"

"Originally, punishment should be something one hates the m-."

"Th-That! No knuckles, I mean, that's, um, that's not it, but, knuckles are
a no, that's, there's a reason why knuckles are a no, so, uh, ah! There,
back then, those bastards kept hitting me on the head with their
knuckles, so if I get hit there, I remember that time. Yes, that's why, so
knuckles are a bit hard, too hard for me to endure."

She hesitated a lot, but the explanation that came out was quite
harrowing.

Qing was startled.

"Ah. I didn't know that. I'm sorry. I must have been inconsiderate to
make you recall such painful memories. It must have hurt a lot."

"No, no. Then! Then, if I use wicked words, you'll punish me? I, I can
receive punishment, right?"

"Young Lady Moyong. You have to be careful on your own. It's not right
to learn by being punished all the time, like some child. Also, what
gives me the right to punish Young Lady Moyong?"

"Th-That's, I don't think I can do it alone. If Young Lady Ximen helps
me, if I feel like I should be punished, then firmly, firmly…… Yes,
firmly, I'd appreciate it……"

If she puts it like that…

Still, she has the will to correct herself, so that's commendable, isn't it?

Creak. This time, the sound of the door opening was timid. Qing turned
her gaze and saw Sima Chunbong, who had readjusted her clothes and
returned.

Woah! Goodness gracious! What a sight to behold! High peaks! Deep
valleys!

She hid her strengths! Really hid them!

But now she doesn't!

Though Mount Tai is high! Under the heavens! It is still a mountain!

Then, a great realization struck her.

Wow. I really do like them big.

She wasn't showing them off like that Lil' Miss Lily or whatever, but just
their presence alone was, wow. Wow.

Qing's mouth fell wide open.

Her jaw practically dropped to the floor.

It was then.

"Y-You, pig bitch!"

Moyong Juhee shouted again, unable to control her bad habits.

It sounded a bit awkward, probably because Young Lady Moyong was a
bit intimidated by such a… ahem… size.

"Sigh. Young Lady Moyong, are you going to use foul language?"

"Ah. I did it again. Then, a, a little pinch."

Qing after hesitating, she pinched the flesh of Mo's side between his thumb and forefinger.
and twisted it slightly, an act called pinching.

"Ouch. B-But, you see, if there are marks on my side, people might see.
Could you pinch me somewhere that's not visible……?"

"You're quite picky for someone receiving punishment, Young Lady
Moyong."

"I'm sorry, I'm sorry."

"You should apologize to Young Lady Sima, not me?"

"Uh, Chunbong-ah. I'm sorry. I'm sorry. For saying harsh things……"

However, Sima Chunbong, who was being apologized to, did not have a
pleasant expression. She was always a beautiful woman, but her
expression was never quite pleasant.

"You should not call me by my name."

"Young Lady Ximen. Her name is Chunbong. It's so countrified, don't
you think? How can a person's name be Chunbong?"

"Young Lady Moyong, you should not make fun of people's names. Are
you going to be childish even as you get older? Do you want to be
punished again?"

"Ah. I did it again. But it is countrified. No matter who hears it,
Chunbong is coun-, ouch."

Since she said somewhere not visible, Qing pinched the flesh above
Moyong Juhee's elbow, to be precise, a bit further inward.

"But, it is, really, coun-. Ouch, it's coun-tryyyyy."

Honestly, getting pinched above the elbow really hurt to the point of
tears.

Qing knew this well because there was a crazy teacher in middle school
or high school who used to pinch that exact spot.

But since she wouldn't change her opinion despite the pain…

Is she not in enough pain? Should I pinch harder?

So, Qing tried to put more strength into it.

"Ack, I'm, I'm sorry! Young Lady Sima, I apologize."

Only then did Moyong Juhee apologize sincerely.

Sima Chunbong smiled in satisfaction at the sight. 