\chapter{Hundred Demon's Night Parade (2)}

\textit{On the other hand, I wonder if I came all the way to this distant Changbai Mountains just because of some baseless rumor.}

\textit{Might as well take a look at Heaven Lake while I'm here, right?}

\textit{How many chances do you get in life to come this far?}

Then a thought suddenly occurs to her.

"Elder, by any chance—"

"Why so formal? Call me Uncle. You're my daughter's one and only friend, and I'm not even that old."

Uncle (伯伯) was at least a respectful way to address a friend's father.

A more familiar term would be 'Uncle' (叔叔) with the surname attached, but for someone from one of the Five Great Families that might be a bit too casual.

"Ah, yes. Uncle."

"So, what is it?"

"Ah, by any chance, were there any folktales or legends among the Jurchens, about monsters with strikingly dark veins?"

"No. To begin with, the Jurchens don't even have monsters in their folklore. There are plenty of evil spirits and ghosts, but no physical monsters."

"Hmm…"

As far as Qing knows, no such monsters existed in Zhongyuan either.

And since there was none in her homeland, they probably didn't exist in Joseon either.

\textit{But according to rumors gathered by the Xue Merchant Guild, there were definitely sightings of a monster resembling the Reverse-Blood Demon.}

\textit{Isn't it quite possible that the Blood Demon exists separately from the current plundering party in the Changbai Mountains?}

\textit{So then.}

\textit{Hmm, if I want to investigate, the fastest and most accurate way would be to ask the people in the Changbai Mountains.}

\textit{Looks like I'll have to go after all.}

Murong Chengyi, who saw Qing lost in thought, let out a hearty laugh.

"They call it a 'Night Parade of a Hundred Demons', but it's not really a big deal. Just some petty squabbles. Life is tough for those barbarians. And even then. they mostly fight among themselves, rarely do they target Zhongyuan folk."

For the record, 'Zhongyuan folk' here refers to tax-paying subjects of the empire. The slash-and-burn farmers in the Changbai Mountains who don't pay taxes don't count.

After all, those farmers weren't on census records, so technically they weren't subjects of the empire.

The barbarians targeted these farmers, but they almost never dared to touch proper Zhongyuan merchants or villages.

"By the way, let's spar after dinner. It's a bit embarrassing to say I'll check your progress and then not follow through, but I'll be away for a while."

"Going far?"

"No. I'll still be nearby. Hmm."

Murong Chengyi hesitated for a moment before lowering his voice and whispering.

"I'll likely be going to observe Princess Yuansui's marriage procession. That's why the usually lazy governor came in person to ask for my help."

"Ah, the marriage procession."

Qing remembered hearing about Princess Yuansui's marriage procession before leaving.

Since she had been waiting for Murong Chengyi for a while, he must have been delayed by discussing it with the governor.

"Recently, Beijing has been acting suspicious, so the Alliance has been on edge. This request is probably the Imperial Palace's response to that. If it's about keeping the peace, even with 'No Interference in Martial Affairs' it can't easily be refused."

He was anxious because Imperial Palace couldn't interfere with Wulin, but he didn't know what change of heart caused them to show this kind of appearance.

Murong Seongik added.

"Ah, hehehe…"

Qing scratches the back of her head.

Qing's expressions were an open book to those within her circle.

Murong Chengyi gave her a puzzled look.

"Why do you look so sheepish?"

"It's. nothing really. Hehe."

"……?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Shenyang's signature dish was spicy stir-fried chicken.

The famous Shenyang-style chicken!

In Zhongyuan terms it's called Shenyang Jijia (瀋陽 雞架)!

Of course it's not the same as the spicy chicken from Qing's homeland, this was Zhongyuan version of Jijia.

Jijia refers to chicken wings and ribs, and Shenyang Jijia was made by deep-frying the bones and then stir-frying them with seasoning.

Naturally, Qing had already eaten plenty.

Local specialties were usually enjoyed throughout the region, so she's had her fill since entering Liaoning and heading to Shenyang.

Was it delicious?

Fried chicken. Need we say more?

Qing's meals were hearty, and her enthusiasm for this fried chicken wings-and-ribs dish has long crossed the line.

First, separate the wings and ribs. For the ribs, scrape off the meat with your front teeth to enjoy that perfect texture between tender and juicy.

When you put the drumstick in your mouth and took it out, the bones come out clean.

Put the remaining wings in your mouth whole, and chew them until two bones came out. Done.

A single piece disappeared in an instant, leaving behind a neat pile of shiny bones.

Murong Jun watched the chivalrous warrior devouring Shenyang Jijia with a drumstick in hand.

And since that warrior was his idol, he naturally tried to emulate her, now he can eat with gusto too.

In Qing's words: Now you're getting the hang of it.

Then came dinner.

Murong Jun proudly displayed the hearty eating style he'd learned from Qing.

His father Murong Chengyi was horrified.

"Ahem. Jun. No matter how close you are, she's still a guest. Mind your manners."

"Huh? Why?"

"Swallow what's in your mouth before speaking."

Murong Chengyi's voice was stern.

Murong Jun, who was scolded, looked at Qing with a wronged expression.

"Gulp. But Sister also—"

Qing was elegantly picking at a wing.

Murong Jun stared blankly for a moment.

Even though she was using her hands, somehow she managed to look graceful. Her demeanor, though veiled (a slight breach of etiquette at the dinner table, but Murong Chengyi allowed it to tease Jun) exuded an air of elegance.

The Ximen Surin-style beauty act: How to Eat Chicken Gracefully!

When eating bony food, it was actually unsightly trying to pick them with chopsticks.

Boldly use your hands, and stay beautiful.

No matter how close they were, even Qing wouldn't go full beggar-mode and shoveling food into her mouth like a starving man in front of her friend's father.

"…Sister?"

"Uncle. A child should eat like a child, isn't it charming to see? But Jun'er, you should swallow your food before speaking, okay?"

A voice echoed in Murong Jun's mind.

'Hehe, delicious, so delicious!', spoken with a mouth full of food.

"…"

A sharp pain pierced Murong Jun's chest.

\textit{What is this feeling?}

Murong Jun, twelve years old.

The boy experienced the sting of betrayal for the first time.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Murong Chengyi's title was Ri Yue Xiangzhi, Sun and Moon Existing Together. This symbolized the unique Qi Cultivation technique of the Murong Clan's Heaven Earth Invicible Divine Skill\footnote{乾坤無恙神功; Qiankun Wuyang Shengong} which embodies the duality of opposing energies.

For the record, title evolve with one's mastery. Before reaching this level his was Erjian Yirin, Two Swords One Person or Dual-Blade Swordsman.

Among friends, he wasn't called Erjian (Two Swords) but Yijian (Barbarian Sword), thus earning him the nickname Yijian Yirin, Barbarian First Sword.

Had Qing known, she might have been shocked, wandering how can a person's alias be 'Barbarian'?!

But she didn't realize it was tame compared to her own master's title.

Anyway, Qing rolled.

Rolled and rolled again.

It was inevitable.

Murong Chengyi might ranked the last among the Profound Realm masters, but he was stil a Profound Realm master.

Moreover the spar was heavily stacked against Qing.

When facing an Orthodox faction elder, it's not like she could just unleash Demonic Arts.

Ximen Qing without Demonic Arts?

Like playing xiangqi\footnote{chinese chess} without the chariot, Go with a nine-stone handicap, yabao\footnote{压宝. A type of gambling} while blindfolded or gupai\footnote{骨牌} (ancient mahjong) with five tiles missing.

Moreover, Murong Chengyi was a master of Grafting, and Murong Family's Shifting Stars Transposition technique took this principle to its extreme.

Originally, the true value of grafting was revealed when a master deal with a beginner.

So, Shifting Stars Transposition, in Qing's homeland terms, was the ultimate 'bullying the weak' martial art.

That being said, the subtlety of Grafting made it the most effective among receive-and-defense techniques, allowing even a weaker fighter to hold out longer against a stronger one.

How to describe it?

When she swung her sword, the attacks naturally curved out slicing through empty air, leaving her stumbling and rolling three times before crashing.

One sword and one saber.

The dual energies of sun and moon push and pull the enemy's weapon, revealing a single starlight, the North Dipper.

The North Dipper was the axis of the cosmos, the pivot around which the universe turned.

How can a mere mortal defy such majestic rotation?

So Qing rolled again.

Tumbling head over heels until her back hit the wall.

The back of her neck was on the training hall floor, her back against the wall, legs splayed awkwardly on either side of her head showcasing her ample rear.

But only for a moment.

She sprung up spinning backward.

Murong Chengyi stroke his beard.

"Hmm. your energy control and release have surpassed your realm, and your technique is also superb. Honestlt, no one at the Flower Realm can match you. Furthermore, your understanding of martial arts is also excellent, allowing you to draw Imagery skillfully…"

"This girl will listen."

"By the Flower Realm, you should be forging your own path. That's the real shame here."

Ximen Surin's Divine Maiden Sword Art abandoned its original delicate dance-like elegance and transformed into a destructive martial art fit for a conqueror's daughter.

It was the result of Ximen Surin's own interpretation through her own temperament—the Female Mad Dog—and made it her own.

But Qing's Yue Maiden Sword remained the Yue Maiden Sword as it was—

"Perhaps it suits you too well. When a martial art aligns perfectly with its user's nature, this happens. Your skills improve quickly, but you're so accustomed to it that you don't feel the need to change, and you can't even see where you should be going."

The joy of a child swinging a stick wildly was the essence of Yue Maiden Sword Art that Qing had seen.

Her joy lies more in slaughter, but joy was joy!

To put it bluntly, a child imitation of swordplay was like cutting down an imaginary enemy, so Qing's slaughterous joy wasn't so different in essence.

After all martial arts were killing techniques.

\textit{So the martial art are so perfect that I didn't feel the urge to change them.}

Qing nodded in agreement and asked.

"Ah. so what should I do? Should I try to modify it?"

"Truthfully, Divine Arts aren't easy to change. They're called 'divine' because they're near-perfect. Rather than trying to change the Yue Maiden Sword,  it's better to learn something that doesn't suit your temperament and adapt it to your own style."

"Hmm."

\textit{The first thing that comes to mind is Nine Swords of Solitude.}

\textit{Definitely doesn't suit me.}

\textit{But Nine Swords of Solitude are hard enough to swing as is, how am I suppose to modify it?}

\textit{Tathagata Divine Palm? That's just one giant Buddha's palm.}

\textit{As Uncle said, Divine Arts, the purple-border ones, are difficult to change because their Imageries and Movements were already harmonized.}

\textit{So, um, maybe the lower-tier Demonic Arts?}

\textit{What if I modify a Demonic Art?}

\textit{Oh, that's good!}

\textit{Why didn't I think of this before?}

\textit{If I can tweak a Demonic Art to seem non-demonic, then I can even rename it and use it openly.}

\textit{Let's see, something easy…something like One Hundred Eight Asura Sword?}

\textit{Since it was based on beastly savagery, if I modify it around cute animals instead… hmm, would that even be effective?}

Qing was lost in this new train of thought.

Looking at the thoughtful Qing, Murong Chengyi smiled happily."
