\chapter{Hundred Demon's Night Parade (1)}

The first thing one must do when visiting as a guest was, of course, greet the host.

Why? Why was that?

Actually, no explanation was needed.

Greeting the host when visiting someone else's home was a universal human custom across past, present, and future, spanning all cultures whether Eastern or Western.

However the question itself wasn't wrong.

Exploring why the obvious was obvious was the very foundation of exploring nature, and the very foundation of the development of civilization.

For millennia Zhongyuan stood at the pinnacle of scientific and technological development, leading nearly every technological advancement in the world.

Yet in Qing's homeland's history, the center of such technology shifted to the West, and it was precisely one man who altered humanity's fate.

A giant who changed the course of human history.

A man who upon witnessing a falling apple wondered: Why does the apple fall downward? Why doesn't it shoot upward or sideways?

From this simple almost laughably obvious question, 'Why?', humanity's true dawn began.

Of course the East might feel aggrieved.

Being discouraged from questioning the obvious was after all the most convenient tool for rulers to control the ruled.

Take for example the philosophies represented by Confucianism, Buddhism, and Daoism.

Confucianism preached unconditional loyalty.

Conditional loyalty wasn't loyalty at all, so one must obeyed the commands of parents, teachers, and rulers without question.

Daoism teaches the principle of Wuwei\footnote{無為; non-action} and naturalness, which is the principle of unconditional obedience.

The natural state was the highest state, thus one observes nature and memorizes its phenomena, but the why behind it was irrelevant, just blindly believe and follow.

Buddhism was the principle of obedience that promised the next life.

This life was a lost cause, so pin your hopes on the next.

You were suffering? Where in this world was there a life without suffering? Life was inherently suffering. But if you live virtuously, your next life might be better and eventually you'd be reborn in a world free of suffering and be eternally happy.

Loyalty, harmony, obedience.

The perfect trinity of tools for domination.

Now look at those big-nosed Westerners.

What happened to them after they started questioning the obvious?

Nobles were noble, commoners were lowly.

Why? How? We're all human, so why were they nobles and we commoners? That's unfair, why must we obey?

Huh? Thinking about it makes me angry.

No good—let's burn it all down! Can you hear the people sing?\footnote{Either 'The Internationale' or 'Do You Hear the Pople Sing'}

Anyway.

As part of this exploration of nature, we could also explore why a guest must greet the host.

\textit{If I had to say, it was coming from primitive, prehistoric, ancient times.}

\textit{At that time, the line between bandit and guest was thin, as was the line between bandit and host.}

\textit{Thus a guest had to prove their harmlessness and say 'I am not a bandit, so you must not be one either', lay down their weapons, step forward and offer greetings first, only then demanded the treatment of a guest.}

\textit{Moreover. from the perspective of communal survival, undermining the leader's authority could spell disaster for the group's continuity.}

\textit{So a guest showing deference to the host first was in a way a survival strategy.}

\textit{Hah. The liberal arts science never disappoint.}

\textit{Proud of it! Love the humanities! Love love love!}

\textit{Because I studied the humanities, I live so splendidly and respected by all as a peerless master.}

\textit{Let's say I was a science major.}

\textit{I'd have been finished in a minute.}

\textit{'Huh? Where am I? Did I die and end up here? Then if I die again, do I go back? Well, dying first is the scientific approach. Time to die.'}

\textit{Even if I hadn't, it'd be the same.}

\textit{Would I have even mastered martial arts properly?}

\textit{Even if I memorized techniques by brainwashing, 'Why must Inner Qi flow this way? Can't it go backward? Scientific thinking! Let's give it a try!'}

\textit{And then—'What the hell is Qi Deviation?' I'm dead.}

\textit{Even if I survived, what then?}

\textit{Make soap and sell it?}\footnote{'Campfire Cooking in Another World with My Absurd Skill', or any other thousand of isekai title}

\textit{Zhongyuan already has soap, printing presses, and gunpowder for cannons.}

Qing's thoughts drifted further.

Why was Qing lost in thought?

Because she's bored.

Why was she bored?

Because the host still hasn't appeared.

Making a guest wait was a typical example of rudeness and also a power play.

It was a process battle of wills to establish hierarchy, the eye level between two parties and to break the guest's spirit.

Even at the Imperial Palace, how many days did she had to wait just to catch a glimpse of the Emperor's face?

But the Elder Ilwolsangjae she knew wasn't that kind of person.

\textit{What is it? The Elder is late…}

\textit{At this rate—}

Thud!

"Ah, my apologies. Did you wait long? But the provincial governor came in person. I couldn't just rush out because a guest arrived. You understand, don't you?"

\textit{Ah, there was nothing he could do abput it.}

Qing understood immediately.

The governor was, of course, referring to the Liaoning governor, the highest administrative authority in the province.

Dismiss the governor to see Qing?

That would humiliate the governor, and his resentment would surely fall not only at the Murong Family, but also Qing herself.

Of course, we should also listen to the governor's opinion.

If he found out, he'd be furious, rightfully so.

'You made Her Highness wait because you are busy with me? And she's this close? Agh, who are you trying to kill?! Your Highness! I've committed a capital offense! Have mercy! Though it's not really my fault! Please!'

"If it were up to me, I'd come to see you right away. After all, you're a far more welcome guest than the governor."

"Of course. If the governor were to came see me in person, wouldn't it be for some troublesome request? I wouldn't be happy about it."

At this, the Sun-Moon Union\footnote{日月相在; Ri Yue Xiangzhi}, known among close martial allies as Other Tribe First Sword\footnote{異劍一人; Yi Jian Yi Ren;}, among less-friendly peers as Two Swords One Man\footnote{二劍一人; Er Jian Yi Ren}, ninth among the Ten Great Masters of the World, teetering on the edge of the Profound Realm, father of Murong Juhui and Murong Jun, Murong Chengyi, smiled warmly.

"I appreciate you saying that."

"It is as you say. Wulin's junior Ximen Qing greets Elder Ri Yue Xiangzhi."

"Indeed, how long has it been? Two years have passed, yet you haven't changed at all. Hmm? Well, after all, you achieved such greatness at such a young age."

Murong Chengyi nodded to himself then spoke gently.

"Well, in there any difficulties in your training? It must've been dificult with Elder Mad—, I mean Senior Godmother away. If you have any questions, don't hesitate to ask. We could even spar later."

This was an extraordinary offer.

Even though it wasn't his original intention, he felt sorry for making her wait, and she also helped his adored daughter reached Transcendet Realm.

"So what brings you here? To see A-Ji\footnote{Murong Zhuji's nickname}?"

"That's part of it. I also met Jun'er and thought I'd escort him home. He said he ran away."

"Ah, right. The boy's been in a foul mood lately. So I pretended to enter seclusion to let him blow off steam."

"Huh? Why not just tell him to go out and play?"

Murong Seongik grinned.

"Sneaking out is more fun than asking permission, isn't it? With Guard Lu guarding him, there's nothing to worry about. It's not like he'd get beaten up anywhere."

There was also the unspoken calculation: Who in Liaoning would dare lay a hand on a Murong heir?

After exchanging pleasantries, Qing got to the main point.

"Actually, I'm on my way to Mount Changbai. Have you heard anything about strange man there?"

Even it wasn't for Murong Jun, Qing would've stopped by the Murong Family.

Mount Changbai, narrowly speaking, referred to the sacred mountain of the Korean people, Mount Baekdu, in Jurchen territory.

Broadly speaking?

It was also referring to the entire Changbai Mountain Range.

Zhongyuan folk have this odd habit of calling both individual mountains and mountain ranges '山', confusing everyone.

Their land was vast so unless you live nearby distinguishing between a single peak and a range might seem unnecessary.

Or maybe writing 'mountain' (山) only needed three strokes, while 'range (脈) needed ten strokes, so they just abbreviate.

Anyway, with context, it was easy to roughly distinguish between a mountain and a mountain range even with just '山' character.

But in this case, Xue Familiy Trading Company only gathered vague rumors, making it hard to tell if it was Mount Changbai or the Changbai Mountains Range.

So her plan was to ask around locally, and the western Chanbai Range was Murong Family's territory. No one knows the area better than the Murong Family.

Thus Qing waited with bated breath.

\textit{If the answer lies nearby, I don't have to trek all the way to Mount Changbai.}

\textit{Well, I still want to see Heaven Lake, but sightseeing is a far cry from hunting someone down.}

Murong Seongik answered.

"Ah, that?"

Qing's face brightened.

\textit{He knows something!}

"Have you heard anything?"

"It's always intense around this time. But, which strange man are you looking for?"

Qing's expression goes blank.

\textit{Huh? Which strange man?}

\textit{Are there multiple weirdos? Strange weirdos all over Mount Changbai?}

Her confusion was so obvious that Murong Chengyi pressed further.

"Hmm? Didn't you know? Let's see. For now, on this side there are the Luocha, Yecha, Egui, Xingtian, Taotie, and Muhun. The Joseon barbarians have the Bomgeomeori, Gumiho, Baek-myeon Ran-gwi\footnote{white-faced-ghost}, and what was it? Dogabi? And I don't understand Arasa\footnote{Russia} at all. Their gibberish was impossible to understand. Something like 'Baibai Equi'\footnote{白白餓鬼; white-white preta}?"

Luocha\footnote{羅剎; rhaksasa}, Yecha\footnote{夜叉; yaksha} and Egui\footnote{餓鬼; preta} were Buddhist demons.

Xingtian\footnote{刑天} was a headless monster with eyes, nose and a mouth on its chest. Taotie\footnote{饕餮} was a gluttonous fiend and Muhun\footnote{木魂} was a tree spirit.

\textit{As for the tiger-leeches, three types of leech-like creatures, probably Hojil\footnote{호질; shouting tiger; 虎叱; short story in The Jehol Diary, written in 1780}?}

\textit{Gumiho are nine-tailed fox. But a white-faced ghost? Is it egg ghosts\footnote{달걀귀신; Dalgyalgwisin}? Dogabi seems to be a transliteration of Dokkaebi.}

\textit{And what's this Baibai Egui? He said it was Arasa's crooked tongues, so I guess this is also a phonetic transcription?}\footnote{Baba Yaga}

\textit{But what kind of monster festival is this?}

\textit{I'm asking about the mysterious figure of Mount Changbai, sho why is a parade of monster names spilled out?}

\textit{Is this that Hyakki Yagyo thing?}

\textit{Wait, you're these monsters actually exist?}

\textit{Well, there's this cosmic mystery of 氣 (Qi), and people flying, and lightsabers, and all that.}

\textit{So, there could very well be monsters, right?}

Qing gulped.

"Are you saying real monsters appear here?"

"Ah, so you didn't know. If you had, you'd have said 'monsters of Mount Chanbai',  not 'strange man.'"

Murong Chengyi gave a wry smile.

"I'm talking about the bandit gangs infesting the Changbai Range. They disguised themselves as monsters to hide their identity. Most of them are Dongyi barbarians, but there also the Jurchens that living in Zhongyuan, blue-eye-ghost from Arasa and even the occasional bald Woguo\footnote{倭國; Japan}, so it is a mess."

Since ancient times, the Changbai Range has been infamous for brutal Dongyi bandits raids.

But after Dongyi began venerating Zhongyuan as their suzerain, their laws forbade encroaching on Zhongyuan territory.

Yet one universal truth persists across past, present, and future:

A crime undiscovered was no crime at all!

So the Dongyi barbarians disguised themselves as monsters and resumed their raids.

It seemed like a good idea, because soon every ethnic group in the area was dressing up as monsters to pillage, turning the region into a real demonic realm where monsters robbed each other.

"It's a true Hyakki Yagyo out there."

Hyakki Yagyo was a term used in Zhongyuan too.

Its meaning differed slightly from those of Wo barbarians. It described a world overrun by monsters, or rather monstrous villains, like during the chaotic Sixteen Kingdoms period.

Qing blinked.

\textit{What the hell, isn't this a complete mess?}