\chapter{Chaka Salt Lake Murder Case (3)}

The house was cold, so there was no warmth even when you light a fire.

It was a chill that had risen from not having lit a fire for at least a day.

But the subtle, fishy smell that tickles the tip of the nose, in Qing's opinion, the smell of blood among dogs.

As expected, there were bloodstains scattered on the long-legged carpet. There weren't many, but among them, there was a faint trace. was this brain matter?

In that case, the villain would be someone who uses not a sword, but a mace, a club, or some kind of martial arts.

Other houses were similar, some with broken locks and rattling doors, or even broken hinges that have fallen over.

Then, at the southern end, a large warehouse-like building appeared, and upon entering, I saw a salt pot and piles of salt on one side, suggesting that it was probably a workshop for mining salt from the salt lake.

Qing closes her eyes and focuses on her keen hearing.

I quietly close my eyes and concentrate on my superhuman hearing, and all kinds of sounds come to mind.

Whoosh, the sound of the wind swirling; clinking, perhaps there was something like a small bell hanging there; squeak, bang, the sound of a door being hit hard by the wind.

Um, and this? Ah.

In the meantime, there were sounds of people moving their bodies and breathing heavily: thud, whoosh, slap, thud, whirl, slap, slap.

Qing said, his eyes wide open.

"Hey, can you stay still for a bit?"

Can't you just look around normally?

Why was this kid Gunyeong spinning his body around so quickly, spinning around, spinning around, spinning around, and holding an ice sword and aiming it at the air in a series of crazy movements?

"Yes. No. It's dangerous."

"It doesn't seem like someone would suddenly attack from nowhere. No, no. Even if it's a small area, it's still the same. Why were you spinning around and wasting your energy for no reason?"

"You never know where the enemy might appear."

"Can't we just be on guard? It's crazy, and I'm watching."

"Then I'll take care of it."

And then, he showed his back behind Qing's and followed me, walking backwards.

Even on this cold day, within the detection range of the Qing's Awakening Divine Skill, the slender body of Xue-i-ri was clearly visible, covered in a single layer of overcoat.

Swinging your head from side to side? Doesn't your neck hurt? Can't you just look around normally? Your eyes were round, so why strain your neck muscles?

Or maybe Gunyeong's eyes were square or star-shaped, but Hmm. That's unusual.

If you turn your head away, you will likely become distracted and lose focus, and not be able to see what you want to see.

Well, even the border was the weakest.

Gunyeong, how much more insignificant must you be before you were satisfied? That insignificance was truly terrifying.

More than that, Gunyeong was not looking at his feet at all, and if he keeps doing this, he'll fall over-

Before I could even finish my thought, there was a squeak.

The wooden floor, which was usually installed in warehouses to prevent moisture from penetrating, was warped and sagging, making it difficult to walk without your heels sinking in.

"Ugh!"

Xue-i-ri's butt fell backwards with a pitiful scream, but since she was a master of orgasm, she didn't fall that much, so she stretched out her opposite leg to regain her balance.

"Wow."

Suddenly, with the dialogue being obviously unnatural, he collapses on the ground.

It's a classic leap of faith, a leap of faith that seems to be taken by a man who believes without a shadow of a doubt that an upright spine will hold him in good stead.

Where was this? It's impossible.

Qing takes a big step to the side.

A body that pours out as it brushes past Qing.

As Xue-i-ri fell backwards and made eye contact, her already large eyes opened wide as if they were going to burst out in tears.

Xue-i-ri, who looked flustered, fell back down, landing on her tailbone with a thud, and lying flat on the floor.

"Hey, Iri? were you sleepy? What were you going to do if you just lie down on the street like this?"

"I'm not sleepy, I'm just lying down."

Xue-i-ri, who had given a long answer for the first time in a while, lifted her upper body and looked up at Qing while stretching out both arms.

Xue-i-ri was a person with a dull expression on her face, but her fresh indifference is… well, she's been acting cute a lot lately.

To put it simply, he was the typical grumpy uncle type that everyone has experienced at least once, who keeps on teasing the cuter the child was until they start crying.

"What? What does it mean?"

"Hurry up."

"What does it mean?"

"My hand hurts."

"Not even a kid. Okay."

Qing bends down and extends her slender hand toward Xue-i-ri's.

Warm fingers intertwined tightly as if they had been waiting.

And then it just stops.

"Why don't you give me strength? Should I, a weak person, be the one to listen?"

"yes yes."

"Hmm. That's what Iri was doing."

"No. Hurry up."

Qing gave him strength and raised him halfway, but stopped when Xue-i-ri's butt was about the size of a fist.

Qing, who possessed the strongest core muscles in the human race, was able to hang on to a single slingshot in this awkward position without even noticing.

A slight furrow forms next to Xue-i-ri's eyebrow.

And then, as I try to raise my body with strength, Qing bends down in response and maintains the same position.

Before I knew it, Xue-i was barely able to lift her butt while stretching her arms out behind her.

Qing was barely able to maintain her balance, bending her waist more than at a right angle and lowering her body.

Then, the tips of their noses, to be exact, the tip of Xue-i-ri's nose and the particularly sharp end of Qing's facial mask collided.

Suddenly, Xue-i's eyes start to shake violently, and Qing smiles and raises her body.

Xue-i-ri comes in weakly and quickly dives into Qing's arms.

"Hey, come here? Don't you want to relax your hands? I liked the idea of trying to twist my fingers, but were you the only one who's hurting? My hands aren't ordinary hands, were they?"

"oh."

A rare moment when Xue-i-ri was startled.

Qing suddenly thought, huh? Fingers?

Qing poured her strength into the indestructible fist of the Diamond Sword that the Sosu Demonic Power had given her. And it wasn't just any strength, it was the strength of a warrior who could place a female Xiang Yu on a rock.

Huh, the sound of the remaining breath being exhaled.

Xue-i-ri's back bent like a bow.

If it hurts too much, you won't even be able to scream.

Oh my, the sound of Qingdo groaning in pain was really painful.

Gunyeong forgot that even the skeleton was insignificant.

"It's too much, it hurts……"

Tears welled up in Xue-i-ri's eyes.

It was a request that I had to see in tears.

Of course it hurts terribly.

Put a solid stick between your fingers and squeeze it tightly.

It was one of the most effective torture methods to begin with.

"Sorry. I think I overdid it a bit. Does it hurt?"

"Really."

"So, let's just relax and not be nervous and just go with normalcy. If you're too tense, you won't be able to see what you need. And this body was a true master. I can hear most people's movements with just a slight breath."

"yes."

"So, whoever's hiding there, wouldn't you please come out? We don't mean to harm you. We just want to hear about the village's situation and help if we can."

Xue-i-ri's expression, which had been frowning subtly as she held my hand, suddenly turned cold.

"No. Come here. Don't do that. If you need help, I'll help you. Could you please come out slowly?"

Qing clearly heard faint breathing sounds.

So, to make people let their guard down, he showed a rather ridiculous sight.

Of course, it's always thrilling and fun to harass someone, but even the most innocent ones can't ignore the time and place.

But, with a choking sound, the sound died down so quickly that even Qing ear couldn't hear it.

Qing lets out a deep sigh.

"Those of you in the salt kilns over there? Well, if you come out like this, it's going to be difficult. If you continue to hide like that, I'll consider you the villains who brought this village to this state and have you torn to pieces with your kilns."

But there was still no answer.

Qing delivers the final sentence.

"Okay. I'll just count to three. One. Two. Hmm. Two and a half. Two and a half of two and a half. Two and a half of two and a half, two and a half of two and a half of two and a half of two and a half, Hmm, come here? How many times have I just counted to half?"

Regardless, Xue-i-ri was already holding her uniquely cool ice sword and aiming it at the salt pot with a cold expression.

Hmm. Gunyeong-ah. But it's not that palanquin, it's the fallen palanquin next to it.

Damn, as expected of the weakest, such insignificance in every action. What the hell was this.

Perhaps, in the near future, I will have to tell Gunyeong in detail about my insignificance.

Knowing and transcending one's true self was the pinnacle, so if one realizes that one was insignificant, one will probably rise to the highest level.

"Anyway, half of half. Two and a half, roughly speaking, the next half. And then two and a half, half and a half. And then…"

Qing, who was speaking in a gentle, slightly immature voice.

Then suddenly, a cold word.

"three."

The temperature difference was so great that even Xue-i-ri, who was next to him, felt her heart sink for a moment.

After all, those were the words spoken with murderous intent by the master of a thousand years.

It was a fragment of an evil star that the living instinctively feel fear of.

"Okay, just a moment!"

The sound of the salt kiln being knocked over, and the salt kiln, already overturned by the cold, rattles dully.

Only then did Xue-i-ri quietly turn her body and correct her aim, but soon she seemed to quietly lower her sword at the sound of that young voice.

Hmm. They were kids.

Somehow, my breathing sounded shallow and rapid.

I thought you were injured.

One girl, about as tall as Qing's chest, and one boy, just below his forehead.

As Qing took a step forward, he blocked the girl's path with a square Chinese knife, thinking he was a boy despite being a little boy.

The courage was virtual, but my hands were shaking.

Oh, I know that. That super-vibration blade? The one that separates flesh and bone at the slightest touch?

Qing feigns a smile, takes off his fur hat, and pulls down his face covering.

The little ones whose eye sockets were wide and round like bells.

In those eyes, where hostility and fear disappear in an instant, well, at least a pretty face was useful in times like this.

Sure, it's a little thrilling to look in the mirror sometimes, but that's just a secondary factor.

Kids originally thought that if they were pretty, they were kind.

Although she was so beautiful, she has no expression, so the kids would be scared of her.

"Oh, guys. Aren't you cold? Your lips were really chapped. You didn't even wear a hat when you came in? Oh my, it must be really cold. Come here."

Qing takes off her coat and puts it in front of her, gently trying to calm the children.

The children seemed quite relieved by that sight, their shoulders slumping.

"There is a blanket."

The boy answered, then pulled out a thick, downy fur coat from the fallen salt kiln and put it on the girl.

Judging by the condition of the house, it must have lasted more than a day, and it seemed like the secret to surviving this cold winter was this.

"Hey, you're taking care of your own woman? This was so manly. Man, that's cool."

"…She's my younger sister."

"Ah. Hmm. Right. You're the older brother who takes care of his younger sibling."

\textit{Isn't your younger sister quite tall?}

\textit{Did she eat all of her brother's food by herself?}

\textit{Looking at how much her brother eat, I think he might have given all his food to his younger sibling.}

\textit{Or maybe the parents only fed their daughters because they didn't need any sons.}

\textit{Now that I look at it, the lips were very blue, very similar, um, not similar, but cold.}

"Oh dear. Come on, let's start a fire. You don't have any manure? Guys, there's a pile of manure here—"

Then, the little boy's very frightened cry cut off Qing's words.

"No! If you light a fire, those bastards. Those, those bastards might come, no, they will come!"

Those kids.

The sight of flocks of birds gathering together in a disgusting manner flashed through Qing's mind.

As expected, some kids were causing trouble.

In the center of Qing's eyes, in the pitch-black abyss, a ray of ominous color stirred.
