\chapter{Chaka Salt Lake Murder Case (11)}

Qing floated gently.

It was an elegant figure that seems to fly rather than jump, as if it was rising against the laws of the world and rising into the sky.

It was a unique anti-gravity walk of the Moon Lady Walk.

A peak that came to mind like that.

Qing's body suddenly spins around.

I lowered my posture by placing my feet on the spot where my head was and bending my knees tightly, as if I were squatting upside down with my feet on the sky.

Qing's gaze, which had raised its head, met Na Cheok, the great master of the Hyeolryeumsa Geumgangseung.

Suddenly, Na-Cheok feels a chill and without realizing it, he holds the stone tablet tightly with both hands and holds it out.

Yeah, block it. I want you to block it instead of avoiding it.

Bang! Qing kicked the air and shot out like a wedge or a shell, its head forward.

The flexible body of Yuryuyeonyeon, with the right hand bent back as if the shoulder was almost gone, and the vicious thorn of Nangabong pulled up to the max.

This was, so to speak, a grand fall.

Kick through the air and fall to the ground, then swing the iron hammer with all your might at the moment of impact to reduce the impact on your body.

In other words, a properly unfolded attack was a blow that contained the entire power of the fallen star.

A new type of blue bullet that shoots at the same speed as iron bullets that can easily pierce through iron plates.

Only when it reached close range did the thorny iron spikes of the Nanga Peak, hidden by the body, rush in as if connecting the space -

The fear that appeared on Na-Cheok's face.

I quickly jump backwards, barely grazing my toes as the star falls.

-… … !

The earth shook violently as if it were about to collapse.

A translucent ring expands rapidly, spreading out into the world, followed a beat later by a whoosh of wind.

Urur, Busususu The houses in the alley shake with an ominous trembling, scattering stones.

Gyeongcheon Daeseongmagon, Palcho. Yooseongrak.

Humans were nothing more than insignificant creatures before the earth, the sky, the celestial bodies, and the stars.

Who would dare to oppose a falling star?

But what if you avoid it?

The impact was so strong that it made the frozen ground cave in. Amidst the scattered pebbles, Qing fell to one knee and supported himself with his bare feet, his eyes wide as he held the human shield.

Na-Cheok, who had been lying on his back with only his upper body raised, was met with a gaze that was full of menacing murderous intent.

"The world's best killer-"

"What the hell were you talking about, saving my life! were you suddenly begging for your life, you cowardly old man!"

Qing screams and jumps up.

Na-Chuk was shocked before the crisis.

I just wanted to say that it was the world's greatest murder.

But wouldn't that make it seem like you really asked to be spared?

"who-"

"I just asked you to save me!"

Qingi, wedge the Nanga Peak vertically!

Na-Cheok quickly turned over and rolled around.

It was a method of Naryeotagon that was said to be more humiliating than death.

I don't know why such absurd things were said, when there was no one in the world who has not rolled on the ground in danger.

Bang, bang, bang. The hammer strikes the ground, recoils, and strikes the ground again, repeating the process.

The Qing's offensive, which was like catching a mole, was constantly pounding the ground.

It was pitiful to see the old monk rolling on the floor, crawling, and jumping around like a frog.

So it seems the disciple couldn't stand his teacher's misery.

"Go! Where!"

With a shout, the lama extends his hand.

The bloody palm slowly flickers, disappearing into space and regaining its color.

But since we had already made plans.

Qing raises his shield and faces the bloodsucker.

A human shield whose prayers were already torn and unable to make a sound, but whose expression expresses its pain.

"[What, what, what……!]"

The lama who had thrown the blood seal was so shocked that he could not speak, and he froze with his hands outstretched, his eyes trembling.

A hand grabs the lama's sleeve for a moment.

Jian Buxi, who only looks at Qing, joins faster than anyone else.

As the hem of Parak's clothes flutters, the body holding the arm spins around five times and the crushed arm falls limply as if the bone has disappeared.

The price to pay for losing your eye during battle.

"Inom!!"

With a fierce roar, Na-Cheok's hand, which had been crawling on the floor, draws a familiar shape.

The index and middle fingers were brought together to mimic the shape of the Buddha's hand. Ss …

The essence of nature gathers together to be seen.

A strange technique that was impossible without thought.

In an unusual move, Qing, sensing danger, immediately tramples the ground.

Black, acrid magic energy rises like dry dust, and Qing sky soars, rapidly widening the distance.

The eyes of Qing and Na-Cheok, floating in the air, meet.

An old man with a creepy smile.

The energy of the invincible water seal continues to swirl in one hand.

Qing, oh no. I got fooled by that old man.

From the beginning, it was a method that took a considerable amount of time to produce.

By withdrawing on his own, Qing ended up buying time.

Soon, a bright red energy exploded out from Na-Cheok's hand in all directions.

In an instant, Qing bird that had been soaring high stops in the air.

He quickly turned his body over and lowered his body to the sky, in the posture of the Great Heavenly Demon King Yu Seong-rak.

Na-Cheok looks up, gritting his teeth.

The old monk's hand was shaped like a huge palm with blood-red energy. The huge palm, more than two feet long, growled violently as if it would shoot out at any moment.

As Na-Cheok's eyebrows twitch, Qing kicks the sky again, reenacting the fall of the stars.

I stretched out my hand as if I wouldn't give up-

Oww… … !!

The sound of a huge mantra fills the air.

Oum was a sacred sound spoken in Buddhism, and was recited before all mantras.

Because Oum was the sound that speaks of the foundation of the universe and at the same time was Vairochana Buddha himself, the source of all Buddhas.

And the source of man was blood.

The divine power created by the Hyeolryeumsa, who belongs to the Seojang Buddhist sect that worships Vairocana Buddha as a great Buddha, cannot help but be blood-red.

A huge, bloody palm extends out.

The secret great man, the eight-year-old, the one-year-old Buddha.

The hands of the Great Sun Buddha support the world.

The giant hand of the Great Sun Buddha, Vairocana Buddha, which illuminates the past, present, and future.

Oum - The most destructive source of power strikes the world with the sound of clear wisdom.

A massive destruction that even the Qing, no matter how far beyond the realm, would not dare to confront.

Missed!

Boom!! The loud noise of a meteor hitting the ground, followed by the s …

Left ear?

Na-Cheok's head suddenly turns around.

On the other side, pieces of meat were flying in all directions.

The hostage who had been in a miserable state just a moment ago and the disciple who had been caring for him were now disciples.

Because it ended up being spread out in all directions like a piece of shattered meat.

In the first place, Qing was not the type of person to clash with things that should be avoided.

Some men might say that it was a matter of pride or something and call it a great man.

I'm not a cripple, and I'm obviously using strong tactics, so why were you charging straight in?

In the first place, what was the reason that Qing learned the Great Heavenly Demon without hesitation?

It wasn't because of the power of martial arts.

Wasn't it the maneuverability that allowed it to quickly break away in one direction in the air?

But, um, it feels awesome.

It's a shame to die in one shot, but, oh, this, really, oh, if I do it wrong, I'll get addicted.

"[mean!]"

Leaving behind Na-Cheok's praise, Qing slaps Nanga Peak and strikes the back of another lama who was caring for the chosen hostage.

Far away, this heavy sensation digging into my strong spine. Huh, Qing lets out an involuntary, foolish laugh.

A disciple with a broken back in one room drops his upper body at an odd angle.

An old lama rushes in furiously.

The rings on the stone wall clash and make a loud noise as they rush forward.

Qing dropped the Nanga Peak and thrust the human shield forward.

The stone statue barely manages to come to a stop, along with the strange phenomenon of a creaking sound that seems to be audible.

In an instant, the human shield splits into eight pieces and shoots out in all directions.

Na-Chuk swung his staff in fright at the translucent blue that was rushing towards him, but it just passed through him and he just skimmed through the air helplessly.

When the Heavenly Demon Lord uses the Clone Shuffle Technique, Qing, who has taken a position behind Na Cheok with the exquisite skill of the Nengpa Mibo, immediately throws Nanga Peak.

A thud on the back of the lama monk who was stretching his staff towards Xue-i-ri!

It was a blunt weapon thrown with power beyond human reach.

The moment Lama leans forward, Xue-i-ri's ice sword cuts his arm without fail.

"Inom!"

Meanwhile, Qing's hand stretched out like a rake, and Na-Cheok quickly swung his arm, saying, "Zeng!"

The sound of leather breaking against steel.

Na-Cheok's eyes twitched.

A dark mirror that seeps into the hand that collides with it, a totality of extremely vicious malice that secretly tears and digs into the veins.

Only then did he notice the faint, distorted, whitish shape of the young Kang-gi resting on the back of his hand, like a hallucination.

"You bitch, minority-"

"Wow! What the heck, why doesn't everyone know this!?"

Qingi shouts, cutting off the unfavorable words and continuing the malicious attack of the minority demon.

A loud noise, like several iron bars striking each other in unison.

He was just a nasty scratcher who put up a human shield, so Na-Cheok just kept retreating and retreating and retreating, desperately trying to slap his hand away.

And, oh my… …!

Why, why this sound?

Qing's head suddenly turns.

A giant bloodsucker strikes the ground as if to crush it, like a human shield.

Peng Daesan and Gyeonpohui were in a state of confusion, scattering left and right, barely escaping the range of the highest season, the secret missionary.

The smile disappears from Qing's face.

What, why were there two Hwagyeongs?

I need your help quickly, no, no.

Because neither the mountain nor the hill were children that I have to take care of.

The two of them were one less than the number of people who can take on Hwagyeong, but they will still be able to hold out.

So, let's not be impatient.

Qing threw down a human shield.

Na-Cheok, who was running towards him, hurriedly flew forward and barely managed to catch his disciple who was missing.

Meanwhile, Deeng-!

The sound that awakens Brahma, the sound that strikes the sky, and the sound of the wind striking the nachuk.

Meanwhile, Qing quickly surveys the battlefield.

The number of enemies, which was originally seven, was now three.

One of them was busy dragging the wounded away from the battlefield, and Qing immediately pointed at them and shouted.

"Hey! That kid!"

"yes!"

Xue-i-ri runs to the lama monk who was pulling out the injured person.

But Na-Cheok immediately heads towards Xue-Iri.

"[Where!]" "Where!"

Qing and Na-cheok shout at the same time.

The sunset-colored sword energy on the Moonlight Sword advanced towards the old lama, drawing a long tail. Zzeng!

The sword and the stone, the sword and the gong clashed, and the soles of Qing's feet scraped the ground, pushing him back about two feet.

In comparison, Na-Cheok's body was sturdy.

Even in the same flower arrangement, there was a strict difference between the early, middle, and late stages.

Na-Cheok also realized this and his expression became more relaxed, and his ferocious demeanor increased.

Qing smiles back at him and responds.

Yeah, I know he's not an easy guy.

But if everything was going to be decided by the realm, why on earth would a warrior fight so hard?

Ask each other about your level, and the lower-ranking one should admit defeat and commit suicide without wasting energy.

Qing's left hand extends out to the side.

Deeng-! With a dull clang of the temple bell, the body of the lama monk who had been swaying on the other side was thrown and falls.

Na-Cheok's proud face suddenly changed.

Qing was trying hard not to sound impatient and manages to make a voice that was barely contained.

"See? If I just wait like that, all my precious disciples will die? What were you looking at? Aren't you coming in?"

And then he pretended to point with his finger.

He turned his hand over and folded and unfolded his index finger.
