\chapter{Chaka Salt Lake Murder Case (7)}

A monk was dragged across the alley, tied with a rope, across the frozen ground.

Because the airway was so wide open, no sound escaped.

But the bloodshot face, the dripping blood, the bloodshot eyes. Every muscle in his face twitched and spasmed, a desperate scream emanating from his expression.

"omg."

It seems that the stimulation was quite strong for the residents who came out early in the morning to draw water or salt water from Qinghai Lake.

But there were rare reactions here and there.

Most people pretend not to see it and stand far away.

And then, he carefully looks at the ground, the sky, or the decorative windows of other people's houses, and clearly shows an attitude as if to say, 'I didn't see you because something caught my eye.'

I was faithfully following the teachings of Zhongyuan to avoid getting involved with a man with a sword.

But there were some long-legged people.

He was startled and ran towards the monk, screaming in surprise when he saw his bald head.

And then, when they see the fake monk with the letters carved on his bald head as big as a door, in Chinese and Western script, they spit and swallow their curses, and go on their way again, relieved that it looks good.

"But where were you going? If you find out anything, please let me know."

"Huh? Ah. I haven't found out anything. were you saying that the Blood Thunder Demon's followers were a bunch of bastards who, while searching for the escaped Strange Monk, also committed a massacre?"

"Then what about now?"

It means where were you going now?

San was a quiet person, so he has a bad habit of speaking briefly.

Do you really think that would look cool?

A manly way of speaking?

"Nowhere. The thugs probably dispersed to receive a bed offering, so if you wander down the alley, you might run into one or two of them."

"You walk so confidently, I thought you had some kind of plan."

"I don't know anything about the enemy, so I'll make up a plan as I go. Maybe the enemies were scattered and sleeping? If I venture out onto the main road in this small town, I might run into enemies already gathered. Likewise, with fifteen enemies remaining in this small town, wouldn't I be able to take down one or two before they can unite?"

It was only at times like this that Qing became smarter.

Of course, it's not strange.

Even people who don't usually think much tend to be very creative when it comes to hobbies they enjoy.

If I had to give it a name, it would be something like murder intelligence or slaughter intelligence.

"Hmm."

Peng Daesan, who had nothing to say, said, "Um."

It was a stupid plan to wander around until we encountered the enemy in case we ran into them.

But it was also true that there was no better way.

Criticizing without offering an alternative was just opposition for the sake of opposition. Pang Dae-san was not a petty person who could not acknowledge something worthy of recognition just because he found the appearance of the proud Qing unsightly.

"Should we try to come up with a plan? When we first meet…"

And so, from the cold morning, four people busily moving through the alleyways plus a piece of luggage being dragged around began to repeat the same thing, startling the diligent residents of Cheonjun.

Then, as if by magic, a shiny bald head suddenly appeared at the corner of the fork in the road ahead.

Qing suddenly shouts.

"[Monk! I've found the traitor you were looking for! He's a dangjung who speaks a strange Zhongyuan dialect. was this you?]"

"[What!?]"

A monk with wide eyes rushes towards him in one stride, stepping on the Dharma.

He lifts the rope as if to show his gratitude, and politely holds it forward.

It was at that moment that the monk, in a panic, accepted the rope.

The two hands of the monk curl up like snakes, wrapping around the monk's left and right hands respectively, and climbing up in the shape of a coiled snake.

It was a welcome welcome to the spirit of the spiritless being that had arrived.

and.

Qing arm wrapped around my forearm suddenly straightened!

Crunch! With the sound of bones being shattered, tang. This time, the lama's arm was wrapped around Qing's arm twice.

A person's forearm cannot be flexible enough to wrap itself around another person's forearm twice unless it was made of rubber.

Of course, the arm was crushed and shattered into pieces.

"ugh……!"

Ssaeak, ssaeak.

The lama's screams turn into a mere gasp before they can even gather their full force.

Because at that very moment, Jian Buxi's finger pierced the lower part of the Lama's throat.

They were sisters whose hands and feet fit together very well.

To be exact, it can be said that it was a form of the older sister who always looks out for her younger sibling (only) unilaterally giving in.

Qing raised his arms in that state and cheered.

The lama, whose arms were entangled in a crushing force, was lifted up and swung around, drawing a semicircle and flying through the sky-

"mountain!"

As planned in advance, the trajectory of the sword light on the Pangdae Mountain was drawn.

The lama's lower body attempts to escape from his torso and tumbles far away.

It was the moment when the severed surfaces of his two knees, which had been drastically reduced in weight, struck the ground, and countless bone fragments from his two twisted forearms dug into his muscles.

While the lama was still unconscious from the excruciating pain from above and below, Qing's heel was stuck in his lower abdomen.

After understanding the principle of breaking the danjeon, you can break it very well with your feet.

There was no reason to worry about side effects in the first place, so it was more convenient to just hit the Heavenly Demon Energy with the method of the Heavenly Demon Lord Limbo than with your hand.

"big."

It was a lama who bravely let out a one-syllable scream, as if blood was filling his perforated airway.

I tried to utter just one syllable, and then I spat out blood through the hole in my throat.

And then, Xue-i-ri freezes the severed leg of the lama monk who was writhing like an insect.

Church finished.

Qing nods happily.

A great combination of three martial artists units, and a neat finish by a bystander and handyman.

How satisfying it must be for a leader to see the demons return to their original position as planned.

Paengdaesan has an expression on his face that makes him wonder why this was actually working.

After all, there was no master in the face of carelessness.

Even if Qing, a true master of Jo Hwa-gyeong, uses a mean trick, isn't there a law in Qing's hometown that says you have to be beaten if you don't know? (There isn't.)

There were two fake monks hanging from a rope like that.

"[Monk! We caught a traitor here!]"

Three fake monks.

"[Monk!]"

Four fake monks.

The last one was on guard, so the annoying process of bickering was added.

Well, there's only one traitor, but there were three people brought here, so it's understandable that it's suspicious.

But how long can a high-level lama last against both Hwagyeong and the high-level lama?

Since the result would have been the same anyway, to add to the annoyance of making him feel weak, he cut off all of his limbs and left only his torso.

Looking at the frozen area, Qing looked at Xue-i with a curious expression.

Could Gunyeong be useful?

Of course, I could do it if I wanted to.

They all hold onto each other's ropes and drag the load around, screaming with their whole bodies and facial expressions.

The Qing realized that there was a blind spot in the operation and that they were in a very serious problem.

Gulp! A loud noise like an earthquake.

Miss, I'm hungry…

I guess I learned that for nothing.

After learning that, I've been really hungry all the time.

Hey, that girl, she was so obedient and told me the location of the martial arts, but was this some kind of intelligent trap?

"Hmm. Should we go get some breakfast first?"

"You want to eat breakfast now?"

"Food was a crucial matter, isn't it? It's a value that should take priority over any operation. It's also a matter of humanity and dignity. Don't you know that a general who fails an operation was forgiven, but a general who fails to supply the troops deserves to be beheaded?"

"This was the first time I've heard of it."

"No, you don't even know the basics of this strategy? San, this was disappointing. Have you heard of Yi-mei?"

"Ugh."

That doesn't mean "Jian Buxi's eueung" was wrong. Hmm. Please adjust a bit. Yi-mei was good, but she needs to be a bit more tactful.

Qing looks at Xue-i this time.

"Have you heard of this?"

The fact that Xue-i-ri's eyes were shaking caused an earthquake, indicating that she was experiencing a serious internal conflict.

And then-

"D, I've heard of it."

"Oh, you're so kind, come here. Come here, let's hug."

Qing giggles and hugs Xue-i-ri, stroking her head a few times before making a serious expression.

"Hey, just kidding. Even if it were me, I wouldn't stop what I'm doing and eat at this point."

Now that it's all out there, I don't think more will come out just by walking around.

All the guys who want to join will have gathered.

So let's throw these in a suitable place and see how they look.

"Besides, even if they're bastards, they wouldn't go on a rampage in the city trying to kill everyone. It's not like they can just wipe out a village."

If they realize that their comrades have disappeared, they will surely scatter again to search for them.

If you follow them and cut them down, when their numbers were reduced, you can attack them or do something else.

Pengdaesan was purely amazed.

To be honest, it feels a bit unfamiliar.

So, I returned to the first house and threw the monks there, and froze them once more to prevent them from melting and bleeding to death.

Although escaping would be impossible anyway, just in case, I knocked over a blanket in front of the bedroom door to prevent it from opening.

Even after going this far, you still escape?

Humanly speaking, then we should just let it go.

If you can escape from a locked room in a locked house, with all your limbs crippled, Qing was willing to let you go, applauding your human victory.

If you can, by all means.

Then, we decided to sit down at a street stall near the square in the middle of the city and enjoy a slightly late breakfast.

"First, four bowls of barley porridge."

"I'd like two bowls."

"Come here. Let's eat and order more. The porridge was getting cold."

"ah."

Xue-i-ri, who would go crazy if told to kill her, was greedy, but what good would it do if she ordered it in advance when it's cold outside?

"Sir, may I buy some side dishes from another stall?"

"Well, since we're all trying to make a living, it would be nice if everyone sold it."

The owner readily accepted, so Qing walked around the square and collected bowls of various types.

Even so, there weren't many varieties: milk porridge, noodles, a plate of stir-fried dried vegetables with dried meat, and a plate of grain powder on a small table.

As I was enjoying my leisurely breakfast on the cold street, people began to slowly gather in the square.

As the number of people wearing the traditional Jang people's outer garments, called chupapuru in the headman's language and chuba in Chinese, gradually increased, they suddenly knelt down in unison to pay their respects, and the lamas with uneasy expressions entered the hall and took their places in the center.

It's obvious that he has an unpleasant expression.

They do it because it would be suspicious if they didn't, but I wonder if they don't want to give a sermon to those who have betrayed their nation.

That number was six.

Of the sixteen in total, four have already been killed, so there should be twelve left. The rest may be searching for the Amukhaprap, or they may have gone looking for their missing comrades.

And so the sermon begins.

however?

"[…A tree with rotten roots can never survive, so it was the natural order of the world for it to rot alive and die a painful death. The root was the soul and spirit, so you must look back and reflect on whether you have been heading toward death.]"

Somehow the content was a bit…

"[We must be careful not to let our Western people follow the uncivilized customs of Zhongyuan. In particular, we must be careful not to let the sons and daughters of the Western people be fooled by their uncivilized calendar and follow it recklessly.]"

Suddenly, the atmosphere changed and Jeong Hoon's education began.

The people who came to hear the sermon also had expressions that seemed to suggest that something was a bit strange.

The monks click their tongues at him.

"[Go! Rather than seeing impure things, pluck out your eyes. Rather than hearing impure things, cut out your ears. If you can't do that, then everyone should cover their ears at home and avoid being tainted by those impure customs…]"

In the end, it was half a day.

Isn't this some really low-level nonsense about how the customs of Zhongyuan were base, impure, and ugly, and that you should reject them and strictly follow the teachings of the Western Master in order to preserve your purity?

Qing whispered to Peng Daesan.

There was no one to ask except Peng Daesan.

"San, those monks, so Arab, Ara? Arabian Naisa?"

"Arab Daltaek Bulshinsa. How on earth can you remember something so twisted?"

"Anyway. Isn't that in Zhongyuan? Then aren't those monks from the Zhongyuan too?"

"right."

"No, those kids were funny. That one."

"That's true."

Peng Daesan readily agreed.

Anyway, the sermon ended like that.

The time of standing in line politely and offering offerings continued.

Only after everything was finally finished did the monks begin to whisper among themselves and then split into two groups and disperse.

The Qing party quietly got up.