\chapter{Chaka Salt Lake Murder Case (9)}

Four of the trout I hunted this morning. Three this time.

I heard that there were sixteen members of the Ddaengjung group.

Nine, excluding the seven cripples.

At least one of them would have to care for the wounded, so the enemy's available strength would currently be less than eight.

It was as if half of the enemy had already been cleared.

But Qing felt a little disappointed.

It would have been better if the group in front, including the old man, had made way for you and told you to go your own way first.

I thought that the old guy there might be the one with the highest level of skill.

I wanted to surprise him with a single blow to the Tathagata Shrine and then run away.

Why, in strategy and tactics, what did they call the command center, the operation to cut off the head? Hmm, there was a term that sounded good. Hmm, um. Anyway.

The correct answer was a beheading operation, and it's as if Qing answered it with his own mouth, but it's not something that falls under the category of general knowledge or common sense, so it's a word that doesn't really matter if you don't know it.

So, I jumped over the house and went to the main road, then quickly dug into the alley on the other side, jumped over a few brick houses, and ended up in an alley somewhere.

The group crouched in the cramped backyard of someone else's house, took a moment to catch their breath and listened.

Even though it was called a backyard, it was only a passageway between the house and the wall that could barely accommodate one person.

-Kwaaak! Where were you! You devilish bastards! I'll kill you!

A loud shout from afar.

The old man's voice was not good either.

A smile appears on the inside of Qing face mask.

Well, there was no praise like this praise, so the enemy's curse was my joy, if I were to translate the old man's cry, it would be for this reason.

"It was truly a daring performance, a bold surprise attack, and a powerful display of skill. We suffered such heavy losses that I was extremely angry. It was such a brilliant move, this old man was shouting, forgetting his age.

Well, let's say that's true.

Why didn't he run away further, but instead hid in a narrow crevice inside someone else's wall, crouching with his back against the wall, his knees touching the wall, a place that, from a carpenter's perspective, was considered cold and windproof?

Well, he looks like a normal lama on the outside, so if you ask him where the guys who just ran away have gone, wouldn't the people of Cheonjun immediately point their fingers and tell him?

It's the principle of hiding behind the door when in a hurry.

-Where were you! Don't hide and come out! Come out, I said! Aaaah!!

An angry shout that was rapidly approaching.

The sound of someone running over the wall.

-Do you think you can run away?! Even if I have to fall into my hell, I'll take you guys with me!

The sound of evil jumping up and down and then quickly moving away.

He must have cultivated his mind as a monk, but he was so swayed by anger.

Of course, a person with mental training would massacre his fellow Jang people, but would not let go of the Han people who were afraid of their supporters.

But the inner strength contained in the shout was still strong.

He must be a master of the level of Hwa-gyeong who will pay the price for the night. Even if he cannot control his anger, he has the confidence to chase down enemies of unknown level alone.

"Let's go, let's go. Hurry up. We have to go now."

Qing urges his party to go in the opposite direction from where the old monk disappeared, taking the shortest route.

Shortest distance.

Take out the bricks as finely as possible and make holes in them.

After Qing crawled on all fours and broke into the house, fortunately the owner of the house seemed to be away.

After placing the silver linings of forgiveness clearly visible next to the gaping hole, he passes through the house, out the door, and through the alley to reach the main road.

I'm sorry to the landlord, but what can I do?

Because you might get caught on the roof.

Of course, it's not like it's impossible to deal with.

Here, there was one master who has transcended the realm, two juniors, and a cheerleader.

On the other hand, the old monk was above the early stage of Hwagyeong and below the Hyeon-gyeong, so even if he reaches the mid-stage of Hwagyeong, he will be an easy winner.

But if it happens that the decision cannot be made so quickly after the Hwagyeong period, other lamas in the city will join in.

So first, reduce the number as much as possible.

I return to the main road, sprint down a familiar alley, and turn the corner.

Then, two surprised lamas.

The expression on your face as if to say, "Why were you here?"

After that, there were people carrying three crippled people on makeshift stretchers, probably people who caught people passing by and made them work for them.

The corners of Qing's mouth were torn apart viciously.

Are you letting your guard down because the enemy has retreated?

"Lightning always strikes twice!"

Qing shouts and bangs! The bullets were fired out, trampling the ground.

The lama quickly raises his staff.

A staff that monks always carry, a red-hot stick with a decoration on the end!

Although they were lamas who responded quickly, they were at their peak.

Boom!! A rough stamping sound that shook the earth.

Not acceleration, but braking. Qing new model, which had been shooting, suddenly stopped in its tracks.

Thanks to that, the stone pillars pass by a foot in front of Qing, and Qing stretches out his finger and points below the lama's dantian.

A single black straight line connects the tip of Qing's index finger and the lama's thigh.

This was the secret weapon of the Heavenly Demon Lord, the Heavenly Demon Death Ray!

A small explosion occurs between the legs, the hem of the pants was instantly ripped off, and the body parts that should have been there were torn apart and scattered in all directions.

The miracle of a man not being a man!

If there had been a Protestant here, he would have immediately burst into tears and expressed his emotion at witnessing the miracle of the Heavenly Demon Lord with all his might.

"Ugh!" "Euuum."

As the remaining lamas took a step back in instinctive fear and Peng Daesan unconsciously let out a low sound, shuddering, another lightning bolt followed Qing.

It was a follow-up attack by Jian Buxi, who unconditionally followed Qing.

The remaining lamas were startled and stab the stone pillars with spears.

But how can one stop a warrior who has reached the peak of his power with only the most intense studies?

The hand of Gyeonpohui, clad in a beautiful peach-colored robe, gripped the stone scepter tightly and pulled it with force, causing the lama monk to lose his balance and come running.

Jian Buxi's palm slapped his cheek! The other foot kicked his ankle, and the lama spun around like he was hanging from a cartwheel, his legs spread wide.

Halfway through the turn, Jian Buxi grabbed Ramasung's arm and he was shocked.

The joint bends and reverses rotation.

He grabs her leg again and slams it into her chest. Then he spins her around as if he's grabbing a steel ball and throws her to the ground.

Geon-Gon-Dae-Na-I.

It was a divine skill of the Heavenly Demon Sect that allowed me to freely control the direction of the force applied to me.

However, strictly speaking, it was not a martial art of manipulation, but rather a martial art of suppressing with greater force, and in fact, it was not a softness but a defeat.

That was the name of the martial art that grabbed the earth and sky and forcibly reversed the natural order.

This was the exact opposite principle of martial arts, which was said to be able to twist a weight of 4,000 pounds or 1,000 pounds with the strength of 4,000 pounds.

Controlling the power of one thousand pounds into the power of two thousand pounds, unleashing a total destructive power of three thousand pounds.

So, the true power of Geon-Gon-Dae-Na-I was the ability to instantly generate great strength, and as the level increased, the instantaneous strength doubled.

As a result, it was an unfortunate study that was left unfinished, reaching a point where the human body could no longer handle the power.

Meanwhile, Qing unleashed a powerful kick to the danjeon of the supremely powerful Lama monk, the Taekwondo Cheonma forced danjeon destruction technique.

The lama, who had lost something precious and briefly lost his mind, now collapses, coughing up blood with his dantian broken.

Qing'er took a step towards grooming herself-

"Oh, no, you guys!"

An old man runs out and blocks the way.

"How can a monk not be afraid of hell? How can this be? In the world."

What on earth were monks to these people?

Qing was about to say that these guys were not monks but just a bunch of murderous cult members, but then he thought that if the lamas came looking for them later, they might end up being harmed instead.

So what? I'm a bad girl.

Qing, with the old man tied to his waist, tramples on the dantian of the highest lama, breaking him.

"Yi-mei, give me one."

"huh!"

The old man who was hanging on the tree was gently shaken off.

Then, he flies away, carrying the fallen lamas on each side like luggage.

Collateral damage continued to occur along the Qing's path, as it would breach walls whenever its path was blocked.

The first time was difficult, but as you continue to break through the wall, the feeling of guilt gradually fades away.

Why don't you give me a generous amount of money for repairs?

Since you have nothing to do all winter, why not kill time by repairing the wall and buying something delicious with the change you have left?

"Huh! What, what!"

"I'm sorry. Please fix the wall with this and use the rest as you see fit."

The now familiar Pangdae Mountain cuts out a golden piece.

The owner of the house, whose face had turned bright red, quickly regained his original complexion.

"Ahem."

Some people collapsed with their legs giving out when they saw the luggage of Qing and Jian Buxi, and some begged to be spared, but they still looked relieved when they were given gold.

The first house I reached after walking down the back alley and into the destroyed houses was where I had stored the luggage I had trimmed in the morning.

Fortunately, there were no hidden ones that had been severed yet, and since the Danjeon was broken so violently, I thought one or two of them would die.

This was truly a tenacious life force.

But it's just withered, it looks like the fever was already boiling and you're dizzy, hehe, it must hurt.

Qing throws the newly acquired bundles of luggage next to the existing ones.

At that, Peng Daesan wiggled his eyebrows?

"You're hiding here? You've caused so much trouble, they'll come rushing in if you come looking for me."

"Hey. Even if we hide, the civilians won't be on our side anyway, so we'll be discovered quickly. They'll probably be prepared for a surprise attack, so it'll be hard to make any moves. And if we leave them alone, they might just vent their anger and massacre us again. These guys were incredibly emotional. So it's better to chase us."

"Hmm."

There was a furrow between the eyebrows of Peng Daesan Mountain.

I thought we would just go all the way out of the city, but that's not it. It's a call to fight.

Let us take risks for the sake of the people.

So I can't oppose it.

This was the fear of justification,

Qing smiles awkwardly.

"I know it's lethal, but let's try to reduce the number as much as possible, and if it doesn't work out, let's just leave. If I had to choose between you and people I don't know, it'd definitely be you guys. But I have to do what I can."

"I didn't say anything."

"Yeah, yeah. I know you're worried."

"Ahem. So, what do you plan to do now?"

"First, let's take care of these."

Qing points his finger at the lamas.

At that, Paengdaesan's expression turned rotten again.

Grooming, don't be so polite.

So, how to deal with the wicked.

Materials: Villain. Rope. Steel. Ice owner.

One. It freezes the limbs of the wicked well.

It was best to freeze your arms up to your shoulders and your legs up to the lower part of your pelvis.

Two. Amputate the frozen limbs with forceps.

If you freeze it first and then cut it, it was hygienic as there was no blood splattering, the ingredients do not writhe, and it also helps a lot in maintaining the freshness of the ingredients without them dying.

3. Wrap the rope around your body and twist it so that it fits comfortably between your shoulder blades on either side of your back to create a handle.

Just be careful not to strangle your neck.

"What the heck was this……."

"Huh? You still don't understand after seeing this?"

Qing lifts the handle on her back.

Then, the limbless body of the dwarf broadly covers Qing sky.

Only then does Qing reveal the identity of the finished product.

"Voila, the shield was complete. If I had to call it a human shield, well, no. It's subhuman trash, so a trash shield? A recycled shield? A bug shield?"

Pangdae Mountain covered his forehead.