\chapter{Chaka Salt Lake Murder Case (5)}

After half an hour of driving on the road and entering the mountain path, we continued on.

Although it was a mountain, there were hardly any trees, and even those that did were thin shrubs no higher than waist height, so it was not difficult to ride the mountain path relying on moonlight.

But suddenly a small village next to the lake appears.

Qing eyebrows curve into a sharp angle.

Of course, it's not a good sign.

Even in the smallest villages, if a fire was lit to add warmth in the harsh cold of the night, smoke would have risen to announce its presence.

But I never imagined that the village would appear until I climbed the hill, because it didn't even have a small presence, let alone smoke.

Qing enters the village with long strides, chewing his lips.

It was a small village with only about twenty buildings. The search didn't take long, and ultimately no survivors were found.

Several bodies were found inside the house.

A few less devoured corpses within the village.

Oddly enough, the number of bodies was quite small, but it was quickly discovered where the rest were.

Corpses strewn along the lakeside behind the village.

It looks like the birds returned to their nests during the night after eating them, making it look even more miserable.

Well, that's not a proper promotion.

The bodies were simply thrown away without any process of collecting them so that the birds could eat them, so they ended up being eaten like this.

Qing examines the pieces of something scattered among the corpses.

"It's a lion's head."

"Huh?"

Peng Daesan lifted a fairly large piece.

Looking at the sharp teeth attached to the lips, she immediately reconized it, "That's Qingdo."

Lion dance.

It was a custom in Zhongyuan during the Lunar New Year to make a large lion mask with a wooden frame and cloth for the body, and then enter it and dance humorously.

It was a traditional dance event where people from the local community select dancers, practice together, and perform together, rather than having professional dancers.

"It seems like they were preparing for the Lunar New Year."

Qing looks around at the debris around him.

An extinguished campfire, spilled pots and scattered trays of champagne, and an abandoned jug of liquor.

It's clear what the situation was like.

People practicing the lion dance ahead of the Lunar New Year.

Since there was nothing much to do in the winter, all the villagers come out to watch together, have a chat, and even bring food and light a bonfire to eat and drink.

Qing sees corpses that were far short of her height.

They say kids have fun just rolling fallen leaves, so how could a gathering where they all play be anything but fun?

If they grabbed the hem of the lion mask and giggled, saying they wanted to do it too, and some of them even struggled while carrying the fairly heavy masks, the adults would have burst into laughter.

"Let's go."

"Sister. Should I give you a hug?"

At Qing's subdued voice, Jian Buxi quietly grabs his sleeve and asks.

"No. It's all better now."

"Ugh. Then, do you want to touch my chest?"

It seems that Qing, who was always dead, was on his mind, and Qing gives him a faint smile.

"I'm just a little angry, not sad or listless. Actually, I'm feeling really energetic. Those kids really won't leave me alone."

But the negative feeling was completely gone, but anyway, Yi-mei's stuff was mine, so why do I need permission to touch what's mine?

Anyway, I feel fortunate to have come again.

If I were alone, I would have rolled my eyes in frustration and run at full speed to catch these bastards.

So we left the village and headed north along the gravel road.

On the way, a half-collapsed tent village appeared.

Fifteen corpses in three tents.

There was only a table full of food that hadn't been cleared yet.

"I guess they had breakfast here."

It was around lunchtime when the lamas arrived at Chajapchon.

And since Chamagyeong collected the villagers' bodies that night, it means that the lama monk had left before then.

And looking at the table in this tent village, there was just one jjamppong, and it was already made by hand, so it was probably breakfast.

Lunch champagne and dinner champagne were served in powder form, and various grain powders were mixed with sweet water, milk, and yogurt, so I enjoy kneading them myself and making various flavors.

So, that means these kids spent the night in that lakeside village earlier.

Are you saying that after killing all the villagers, you calmly slept in the empty house that I built?

Of course, the Nokrimdo who died in the past, the afterlife was unknown, but if it exists, it would be a bit unfair for the bandits who were now paying the price for their sins by being roasted in hellfire and eaten by demons to hear my true feelings.

As the night deepened and drew to a close, we passed another village, or rather, a village, along a small stream.

Looking from the top of the hill, the sky was slowly turning a deep blue, and the wide plateau spread out between the mountains was spread out again below.

And in the distance, a fairly large, well-to-do small town was established.

The group looked at each other.

After spending a whole day in the salt kiln, the Chamagyeong and CHenano siblings met the Qing party.

The lamas have already annihilated three villages and were moving north, so they may still be in that city.

"I wish they were here."

Of course, I can't guarantee anything.

If you listen to Cha Ma-gyeong, he said he was looking for a traitor, so he may have taken a detour and gone in a different direction.

The original purpose was probably not to exterminate the villagers, but to search for the traitor.

But why? Just being humble?

For some reason, what was the reason?

You'll know when you hear it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Cheonjunhyeon, located on the west side of Qinghai Lake, was located in the middle of fertile farmland on both sides of the Pohap River, which flows between two mountain ranges.

Because it was located between mountains, the temperature was mild and the soil was fertile, making it one of the few villages in Qinghai where you can see mountains covered with neat trees.

A village surrounded by fertile farmland and a clear river was bound to grow naturally, which was also the reason why it was quite prosperous even though there were no roads leading to anywhere else.

"Hey, you came over the mountain in the middle of the night? Aren't you cold? Come in."

It wasn't quite a gate, but the middle-aged man guarding the wooden gate looked down at the Qing party and quickly opened the gate.

In times like these, the people of this town were quite innocent. If it were Jungwon, they would have told me to wait since it was not yet time for Shijin to open the gate.

Of course, the flexibility of Zhongyuan people was the best in the world, and a few coins can replace the trouble of opening a door.

"By any chance, have you seen any lamas?"

"Ah. You mean the monks of Arabdaltaekbulsinsa? You had them last night, right?"

He looked at the Pyeongdae Mountain.

Because I automatically turn my head when I hear a word I don't know.

The reason I insist on seeing Pyeongdae Mountain was because Jian Buxi and Xue-i-ri were more ignorant than me to begin with… … .

Of course, Peng Daesan was the weakest among the many brilliant intellectuals, but what can be done if no one puts their brains into organizing the personnel?

- Blood Thunder Cult. This was the sect that the Strange Monk monk belongs to.

Fish cake? Why was fish cake here?

Ah, the chief said he would stop the conspiracy, but even though he was a step late, he may have noticed the bloodshed or was trying to stop it by some means.

Then suddenly a thought occurred to me.

Surely there were several of Eomuk's disciples among that group of thieves.

But was that really just a personal deviation?

What if that's not the case?

What if the Eomukne sect was also in a state of false rumors, like that of the Tibetans?

And then you become a traitor.

Yeah. They said they were looking for a traitor.

Mr. Fish Cake, were you being chased?

It was only at times like this that Qing's head started spinning.

Qing pretends not to know and asks in a clear voice.

"Do you know how many people were here?"

"There were sixteen people."

Sixteen guys.

I don't know how skilled the guards are, since they haven't learned martial arts.

"So where were you now?"

"Oh, you came to see the monks? Well, I don't know where they've been. They might be in the guest house, or someone might have provided them with a place to sleep."

However, it was a neighborhood that was not particularly connected to anywhere, so it was rare for vagrants to visit.

So, even if we call it a guest house, there were only three, and even then, they were not that big.

"Well, you're still inside, right?"

"I didn't hear anything about them going out at night. I don't know if they went out through the East Gate, but I don't think they'd go out in the middle of the night, do you?"

The guard said that and then said, "Ah!"

"Since you've stopped by, why don't you give us a morning sermon? I think we'll see each other if we wait in the courtyard."

"Hehe. Thank you."

Qing hid her feelings and let out a bitter laugh.

Well, judging by the amount of work he's done, I doubt it.

Would those who beat and kill people of the same breed really preach to receive merit?

Now that I think about it, well, then I guess there's a high chance that it'll be in the guest house.

The expression for fish cake was 'accepting an offering', so wouldn't receiving a place to sleep also be an act of bestowing virtue?

Likewise, since they wouldn't want to do good deeds, they would be paying a fair price to stay at the inn. Obviously.

I thought so.

"Welcome! It's so cold out here so early. Would you like breakfast? Or just a room?"

"Oh, that's not it. I was wondering if there were any Arab…um, lamas staying there."

"Ah. You were strangers, aren't you? Why would they come to the inn? They would be there to offer each other blessings. Why would they stay in the inn while leaving other living beings behind?"

"Hmm."

It seems like he won't be staying at the guest house.

Qing's eyebrows twitched.

If Amukhaprap was hiding here, he was probably receiving the utmost hospitality in a private home somewhere.

If that's the case, then the lamas would have wanted to disperse and go into houses here and there in the city to investigate, rather than staying in guest houses?

It was a request that changed the conclusion in an instant.

So isn't now the opportunity?

There won't be sixteen of them in one house, so they'll be scattered all over the place.

But do you know where it is?

Well, you just have to be a little shameless.

And Qing has a thick enough face.

Knock, knock, knock! A man who had just woken up from a pre-dawn sleep opens the door, his expression half sleepy and half nervous.

"What's going on?"

"Oh, I heard the lamas ate it yesterday. I have something I need to deliver urgently, but I don't know which house you're in, so I wanted to ask if you're inside, even though I'm ashamed of it."

But the man's angry expression naturally disappeared, and instead he was shown with an embarrassed and apologetic look.

Since the decorations of the long tribe were hung in front of the house, it must be a long tribe, and this was precisely the feeling that the long tribe has when it comes to serving monks.

Those bastards who would wake up at dawn and immediately kill that child.

"Ah, ahem, then. That guy Abong brought someone over. So, in the second alley over there, no, wait a minute. I'll show you around myself—"

"No, it's okay. I'm quick because I've trained in martial arts. Just show me where to go."

The man who was about to rush inside was stopped and given instructions.

Enter from the second alley on the left and when you reach the fork in the road, go left.

Third from the right there.

A house with blue carpet decorations.

So the group stands in front of the house.

As expected from a cold neighborhood, the doors were thick and hinged, not sliding.

Qing carefully pulled the doorknob, and the heavy latch held its weight.

There's a high probability that enemies were present in this house. There's no reason to wake them up by knocking on the door.

But the door was locked. So what?

So Qing reached for the hinge on the wall opposite the doorknob.

When combined with the unique strength and the indestructible prime number of diamonds, it becomes an invincible extension.

How could the primitive ancient hinges, made by inserting wood into a groove, stand before the invincible extension?

As if breaking a tree branch, Qing's hand tapped, and soon the door, which had lost its hinges, leaned comfortably against Jian Buxi, who was supporting the door, and put its weight on it.