\chapter{Chaka Salt Lake Murder Case (13)}

But sometimes, we have to be fooled even though we know it's an obvious trick.

What if the Qing's cry was false?

It would only end at the level of giving up the initiative in exchange for taking a quick glance.

If there's a real Strange Monk hiding, you'll have to kill it with your life, not with the initiative.

Na-Cheok turns his head quickly and looks around.

Of course, there was no such person.

And Deeng-!

The sound of the majestic temple bell, Na-cheok, oh no!

A stone sword swinging in all directions with its teeth clenched.

A net-like net covers the old man's entire body, filling all four sides to prepare for the clash of the battlefield.

Are you prepared? No conflict?

Ugh! A painful groan echoes through the air.

In Na-Cheok's field of vision, he sees Jang Je-Ja's side bent like a bow, and Pang Dae-san and Gyeon Po-hee rushing in without missing a beat.

"mean!"

"Old man! Who talks about meanness?"

"What-"

"When you massacre innocent civilians who don't even know martial arts, were you fighting fair and square?"

Qing says this and swings her sword.

The first half of Moonlight Sword was a dizzying, unpredictable, and naive trajectory.

Qing's expression was not innocent at all.

Na-Cheok's hands and feet were tangled up in a mess.

One step back, one step further.

He was constantly stepping back, swinging the staff he holds wide with both hands, and was in a hurry to strike.

Bang! Bang! Bang! The yellow swords that were coming in from all sides, vertically and horizontally, collided with the stone wall, making a loud noise.

What the hell was this, what kind of messed up martial arts was this!

Every martial art has a context.

Originally, martial arts were the embodiment of such images, whether they were nature, animals, or the teachings of the sages.

The strong and the weak, the cheerful and the dull, the heavy and the fantastic, if they were not contradictory, they may be mixed, but isn't there still a center that forms the basis?

When you reach the level of a master of Hwagyeong, you will be able to understand the weapons to some extent, so you can think about the number of shots and sprinkle the first season accordingly.

But what on earth was this swordsmanship?

Even while holding a heavy sword, he swings it left and right, suddenly stabs, and bends it at large and small angles.

It's just a meaningless swing with no depth, like a child swinging a branch to imitate some clumsy swordsmanship.

However, since the impact of the strong energy hitting the ground was quite severe, there was no room for carelessness as each move was properly powered by the powerful Salcho.

Na-Chuk gritted his teeth-

"conflict!"

Bang! The Moonlight Sword sank an inch into the Lama's shoulder.

The sensation of bones grinding and digging into the shoulder blade.

At that moment, an old lama steps on the pavilion and pushes in with his stone pole in front of him.

The middle part of the stone pillar that was erected horizontally roughly struck Qing's chest.

"Ugh."

Qing was hit in the vital spot by an unexpected blow.

I feel suffocated and the air leaks out.

Damn flesh, it's so heavy and useless, it hurts so fucking much!

The source of the hidden martial artists force, when you were out of breath, you cannot exert your true power no matter what posture you take.

As Na-Cheok pushed the stone with all his might, Qing's upper body was pushed out and her butt fell!

Ouch, my tailbone! This was useless too!

Hmph, it was the moment when Qing forced herself to breathe into her shrunken chest.

A long shadow splits Qing's face in half.

A new type of sword that flashes a stone.

Qing one rolls to the left, then hits the ground and rolls three times to the other side.

If you become a master of Hwagyeong, the trajectory will bend while striking, so if you roll in one direction, it was no different from just lying still.

Boom! Fragments of the stone ring precariously strike the floor on the left side of Qing. Pieces of the earth, shattered by the cold ground, strike Qing's coat.

In the midst of all this, Qing was a jerk.

"Amukhaprap! Now! Hurry up!"

"Woman, you're lying again!"

Miss, it doesn't work.

Thump! Thump! Thump! The stone hammer keeps hitting the floor.

Instead of going left, right, left, right, left, right, left, it rolls to the right, right, then stops suddenly.

The world spins around and around, the sky and the earth turning intricately, my mind was racing, and every time the sledgehammer strikes me, I get goosebumps.

At that moment, Qing lifts up the sword.

Zzeng! The moment the stone and the sword collided, Qing, who had let go of his sword, grabbed the end of the stone.

For a moment, Qing's gaze turned to the back!

"Hey, hey! Now!"

Yahippa, the proper roll call of the Strange Monk's chief priest.

There, holding the stone and giving it strength, the gaze looking back was delightful, so Na-Cheok, startled, let go of the stone and kicked the ground, flying.

A satisfied voice that reaches Na-Cheok.

"Oh, it's a moonfish. It's catching well, really."

"You b*tch-"

Na-Cheok, who was about to swear, sees Qing floating in the air and jumps in shock.

A stone staff was a weapon equivalent to a long staff or a gon.

As the name suggests, Gyeongcheon Daeseongmagon was a magic spell.

Park Chan-chung recreates the fall of a star through the sky.

Although it was less powerful because it lacks a heavy iron hammer, it was a powerful attack that cannot be faced with bare hands.

Na-Cheok narrowly avoids it.

Qing one, which has a stone stake stuck into the ground, jumps over the end like a high pole.

And then, both arms were raised in the air.

A smile appears on Qing's lips.

This was a complete reversal of fortune, old man.

Knock knock knock The stone hammer keeps hitting the ground.

The one lying down twists and turns his body endlessly.

A situation where the roles of the hitter and the rollr were reversed.

However, when Qing rolled, I had a sword in my hand, so I could have tried to block it.

But the lama rolling around with his bare hands was busy just dodging without any of that.

Even the Gyeongcheon Daeseongmagon's first meal was not just a single meteor shower that jumps down!

Because it was a martial art created by observing the fall of a star, the original downward strikes were just simple downward strikes.

Bang bang bang, bang bang bang, bang.

Another sound that was occasionally mixed in was the sound of Na-cheok striking the stone with his own hand, which he was unable to avoid.

Na-Cheok, cornered, keeps screaming.

"Shangke! Shangke! [Help me!]"

Then, while the Geumgangseung was beating the lower ranks of the Half-Geom Ssangdohoe, the disciple of Geumgangseung Na-Cheok, whose name was enlightenment, noticed his master's state of being rolled around without thinking.

"[Master!]"

The group was so focused on protecting themselves in front of Hwagyeong's master that they had no power to stop him.

Shangge rushes to Qing in a hurry, and the sound of the Buddhist mantra resonates.

As the new Qing form rises, Shangke, who had been charging in like a wild boar, runs away with the great sword, Shingong, in front of him.

Qing's body rose again into the air, then turned over and looked at Na-Cheok.

Na-Cheok's desperate gaze meets Qing's without averting his gaze.

"Come!"

Na-Chuk's curious cry.

He pulled both palms up to his waist and, shaaak, a formless energy swirled around like a pair of swords. Ah, so that was something that could be used as a large blood palm pair of swords.

however.

Am I the kind of person who goes when you call me?

Qing falls vertically without any strength.

The momentum of the Jiseidae Ilnyorae tree collapsing with a rustling sound.

Na-Cheok's eyes were filled with absurdity.

I wondered if it wasn't an atmosphere where the decision was made with martial artists versus martial artists.

But Qing never agreed.

And above all.

Oww-!

The sound of the great man's words that I have heard countless times.

Na-Chuk was startled.

Because the sound of the Great Man's cry echoing through the air could be heard from behind.

Na-Cheok turns around in a hurry.

A familiar face suddenly appeared in front of me!

Amukhaprap, really appeared.

Na-Chuk urgently drew up his true energy, spread his arms, and blocked it, and then, bang! A loud explosion sounded and a bloody light shot up in all directions.

Na-Cheok's body was pushed backwards.

Then a hand gently supports my back.

"[Shankederya? I'm fine-]"

But the gruff woman's voice returns.

"Isn't it Shangge?"

"Huh-"

Na-Chuk tries to twist his body quickly, but-

Deeng… … !

The law of the Tathagata's body and mind, the Avalokiteshvara.

It was a history of the Qing that has already far surpassed the realm.

As the palm of the hand has already touched the back plate, the sound of the temple bell rings majestically, and all kinds of qualities, some gentle, some evil, some evil, come together to begin a merciless invasion.

The powerful self-defense energy of the Hwagyeong mid-stage blocks and resists, but-

"[Foolish one! The minds of the Buddhist monks who follow the Buddha were filled with nothing but murder and greed, and they were so hideous!"

It was a great wake-up call.

However, in Qing's view, the sight of Amukhap stealthily approaching Na-Cheok from behind, almost as if crawling, was not cool at all.

Crack!

Amukhaprap roughly slaps him in the face.

When you get slapped by a bloodsucker with a strong spirit, your cheek will burst and your teeth will break out.

The face turned around suddenly, the gums were clearly visible, and the broken teeth were sharp, making it look like a vicious devil.

As his concentration breaks and his self-defense energy was disrupted, the Qing's true energy seeps into his spine, melting him into a mushy blood.

My spine had melted by a span, so I was about to collapse as if my knees were giving out.

The thick soles of Qing's fur shoes crushed Na-Cheok's forearms.

Kwaak! The other arm of Na-Cheok, who was screaming, was trampled by Amuk-Hap-Rap.

In fact, even without the surprise attack of the fish cake, it was a game where they had seized the opportunity to win.

If the old man was looking at me with his eyes and saying that he wanted to make a showdown, I guess he must have judged that his chances of winning were low.

In reality, if it weren't for the help of his disciple, Na-Cheok would have already been beaten to death while lying down.

But does that mean that the addition of fish cakes didn't help?

No. I could have won, but my friends were already getting tired.

So, Qingdo was able to welcome him warmly.

"Fish cake? How did it end up like that?"

"It's just a little scratch, it's minor."

"What's a little scratch? You're missing an arm."

The left hem of the robe was tied, and the space where the arm should be was empty, so there was nothing attached.

"It's a minor injury."

"No, if it's minor-"

"That's enough. The story was about what happens next."

I pretended to wave my hand with the only hand I had left.

As Qing followed his gaze, he met the gaze of the remaining lama named Shangke.

Then, Shangge immediately turns around and runs away.

Since there was no chance of winning anyway, it was an exemplary strategic retreat to abandon both the master and the four brothers and take care of one's own safety and plan for the future.

He shouts, "Qing'er-kwang, step on the door and shout."

"That bastard is running away! Catch him!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Shangke's escape did not last long.

Of course, Qing's lightness was a rigorous study that even the Shinto priests acknowledge, and there must have been more than one or two instances of him flying around and causing chaos in the city.

Qing runs and catches up with them, grumbling and killing time, and soon the group joins them.

Since Hwagyeong and Xue-i-ri were both at their peak, it was the same whether they were there or not, so even if they were considered as power outside of their own, it was by no means a power that could be handled alone.

So the city square.

Just an hour ago, the lamas who had been giving sermons and receiving bows from everyone were now hanging from trees, tied with ropes.

They say that life was something you can't predict even an inch ahead, but no one could have imagined that it would change completely in just one moment.

"These were fake monks, who dared to impersonate monks. The proof was in the person of the head monk of the Amukharab Arabdaltaekbulsinsa Temple. You already know the truth about my brilliant reputation."

A few shouts of "Strange Monk!" appear and disappear awkwardly.

It seems that the Jang tribe was probably from Zhongyuan and had not learned the basics of martial arts.

"Are you sure about that?"

"You've already heard the sermons of these fakes. I'm so shocked I'm out of breath, I'm about to go and see the Buddha. What kind of Buddha would separate the people of the Western Plains and Zhongyuan and ask for salvation separately? Remember what these fakes told you."

The expressions on the audience's faces change completely.

Until now, the eyes that were trembling with anxiety were now filled with a clear hostility.

Amukhaprap was a very famous person, and the fact that he was a fake monk endorsed by that famous person makes them really bastards.

Moreover, the stories we heard when we gathered to hear the sermons were all about protecting the roots of the Seojang people, and that those who followed the Chinese language and Zhongyuan customs would be punished by heaven and burn in hell.

If it weren't for that sermon, people wouldn't have been so quick to accept it and become hostile.

The saying, "what goes around comes around" probably came about for a reason.

As much as the Western people respect and fear monks, they also have difficulty with them and fear them, so too does their perception of fake monks rank among the worst of human sins.

The hanging monks were being treated unfairly.

But since I can't make a sound after my throat was cut, even though I feel wronged, I can only make a hissing sound and use evil that was not evil.