\chapter{Chaka Salt Lake Murder Case (12)}

Na Cheok willingly responds to Qing's provocation.

There was no reason to be polite when you say that your disciples' lives will be at stake if you don't come, even if it was a provocation or something.

So the two masters interlock.

There was a common misconception that common people who do not know much about martial arts and foolish warriors who dream of becoming masters often make.

A master's fight would be somewhat elegant.

As they face each other and engage in countless fights without ever noticing the lower ranks, momentum builds and a thick tension flows?

Finally, like long-time friends who have been in sync, their first and second strikes will come together in a taktak fashion, and they will spread the principles of a very high level of martial arts.

No wonder one of the opportunities they hoped for was to witness the fights of these peerless masters.

When tax experts hear this, they were dumbfounded.

An elegant fight was something that only a master can do when fighting a weaker one.

Because you have enough time to think about how your own face will appear to others.

But what was a real fight between masters?

As the level increases, the part that increases more and more clearly was the mat.

The sword power achieved at the peak contains the most destructive starlight in the world, so even if it reaches a higher level, wouldn't the sword power only be more powerful?

However, compared to that, the higher the level of self-defense, the more its functions were multiplied.

It was much easier to just hit the enemy with your body without having to block or dodge a weak attack, and it was also effective in creating an opening in the enemy's defense.

So, when masters of similar skill levels fight each other, a real dogfight ensues.

The stone was extended. The target was the side.

Qing's gaze glanced at Ddaengjung's feet. His center of gravity was on the left. If that were the case, he wouldn't be able to exert much force on the stone sword extended with his right hand. Then, Heocho.

Change? Up or down? Where can a slight jolt cause a major shock? Under the armpit, or in the peritoneum beneath the chest wall?

Qing gives strength to the stomach to prepare for the impact.

As expected, the stone slab twists and deftly stabs the area under his ribs. Qing twists his body to meet the slab with his side.

Pfft, the pain was sharp, but Qing closed the distance by pushing forward with his knees.

Na-Chuk also reacts nimbly to the vicious blow aimed between the legs.

By creating distance, you were giving up the initiative, which provides space and time for a proper, powerful attack, rather than a series of empty promises.

Since that girl was on her knees anyway, she can't properly follow the law, so I can also tie her up and respond.

Na-Chuk twists his pelvis, puts his weight far back on his right foot, and lifts his left leg-

Qing's knee banged against the back of Na-cheok's thigh!

I'm already leaning forward.

It was kept in tight balance without being pushed around.

Of course, neither Qing nor Na-cheok think about these processes in their heads.

In the first place, martial arts were a process of engraving experiences into the body, so they were instantaneous reactions that occur in the unconscious realm.

Qing shakes her upper body and sticks her head out.

The stone sword aimed for the chin struck the innocent neck. The stone sword was a false start. The real move was a sword that extended to the dantian.

Zzung! With each hand clasped together, the two masters' hands violently fling off the energy that was properly loaded.

Na-Cheok stomps his hind leg, and Qing pushes one ship behind Ji-Ik, releasing the remaining career.

It was a sight that showed that there was a clear difference in the realm of the two.

But Na-Cheok was no longer at ease.

What the heck!

When it comes to the flower scene, the gap between the early and middle stages was bigger and more distinct than the gap between the peak and the flower scene.

So, it was ridiculous that he, who was in the middle stage of marriage, should be fighting an equal battle against a woman who was in the early stages of marriage.

But that ridiculous, useless power.

And the joints were flexible enough to rotate in the opposite direction.

An absurd duality that allows one to properly display both the gentle and the weak martial arts of two completely different sides.

The shock was compensated for with a strange strength, so it cannot be blocked by the weaklings of the lower classes.

Because his body was flexible yet strong, he was able to withstand the attacks of the masters that should not be blocked by his body without any sense.

And yet, there were already several strange techniques that require careful attention.

It unfolds the Nungpamibo, which was thought to be just a wild rumor, and flies up and down strangely, and sometimes it even explosively increases its speed while releasing pitch-black magic energy.

Even the new law was like this.

The method of daring to ring the temple bell must be that of the Tathagata Great Heavenly Head of India, whom the people of Zhongyuan call the Tathagata God.

On the other hand, the minority magic was a vicious magic.

I thought it was a fake, but I was lucky that I was able to avoid it by using the iron plate bridge after seeing that the hand was dyed black. It was definitely a magician called Heuksalmajang.

If I had hit him with my body, the match would have been decided a long time ago.

Besides, this girl, the girl called Heavenly Blossom Sword, wasn't she known as a swordsman?

If you give them some distance to use their swords, you don't know what kind of technique they'll use, so you can't just move away and make a big attack that requires preparation.

So, the two fight like dragons and tigers, hitting and hitting each other, causing minor shocks, but the real breakthrough was to watch each other's reactions and hold back.

but.

Time was on Na-Cheok's side.

Qing and Na-Cheok rolled their eyes and glanced at each other as if they were trying to match each other.

Before they knew it, the three of them, Qing's group, were rolling on the floor with their winter coats turned into rags.

On the other hand, the lama who faces him was very lively and even elegant.

Of course, when a master was dealing with a lower level player, he was naturally relaxed and his hands and feet were free to move, so it was natural.

The human shields have long since worn out and fallen into disrepair.

A huge hand that strikes down as if it were going to break your head.

Jian Buxi roughly hit the back of Paengdaesan's neck!

Keuk, Peng Daesan was thrown backwards with a suffocating sound and rolled on the ground.

Meanwhile, Xue-i-ri, who was wearing a Bingryong, hit the lama monk on the back with a proper awakening!

It went into the main event, but the person using it was a total idiot and even an ice breaker.

After the lama took a step back to relieve his shock, he turned around with his eyes burning brightly.

Xue-i-ri, with her characteristically expressionless face, holds out both palms and shakes them sharply. "It's not me. It's unfair."

The tendons on the lama's forehead flared.

The lama kicks the ground.

Boo-woong, boo-woong, a crimson energy was swung wildly with both hands.

Xue-i-ri flies, jumps, and rolls around.

I ran so hard that my hat came off, and I barely managed to survive, panting for breath.

In a fit of urgency, Jian Buxi grabs Xue-i-ri's hair and pulls it violently.

Xue-i-ri curls up with a short scream.

At the same time, Peng Daesan rushes in again… …

Time was not on Qing's side.

The group was barely holding on.

Until Qing came and defeated the old man and helped him out.

However, in a fight between a master and a beginner, the beginner will eventually get tired and fall first.

So, if Na-Cheok just maintains his composure like this, wouldn't the disciple who killed the rats eventually come to his aid?

Oh, really, that's it.

Even if Gunyeong was the peak, I would have thought that Xuegunyeong's Gunyeong would have been Gunyeong in a different sense than that Gunyeong.

No, even though you're so diligent in training, you still haven't reached the peak?

Of course, Xue-i-ri will feel wronged.

It was an unprecedented achievement that he reached the peak of his power in his twenties.

Even in the North Sea, they couldn't stand to see that traitor, so they banished him far away to Zhongyuan.

Anyway, Qing grits his teeth.

If you really do it with a poisonous poison sword.

But that's really a slaughterhouse, no, a slaughterhouse of the flesh.

Since it was a finishing move that cuts down the enemy while risking lying down as a critically ill patient, wouldn't it be a season that can only be used when someone can take care of Qing?

But rather than leaving it to him, I have to go and save him.

Bang! Qing's head suddenly turns.

I got hit hard in the cheek and my vision flashed.

It's a disaster caused by a moment of carelessness.

The moment when Na-Cheok raises his hand over his bald head with a triumphant smile and prepares to kill the weed!

Flash! This time, lightning actually strikes.

A deep purple lightning bolt connects Qing and white waves with the characteristically segmented trajectory of lightning, and then…

"Bicycle-"

"Yes! Rotate! The Earth rotates!"

Qing'er screams and covers Na-cheok's square mouth.

Why was this old man so anxious that he can't teach others about magic?

Thanks to this, Qing barely managed to regain the gap between the swords and drew complex lines in the air with the Moonlight Sword.

If I had to describe it in words, I would say it would be a chatty temple. Imagine how noisy the scene would be with four dragons gathered together.

A sword technique that fills the entire area with energy like a character filled with sixty-four strokes.

Seven seconds of the Moon Lady Sword, Insan Jeongheo.

People were fleeting and fleeting, and organizing was meaningless and meaningless.

The moon woman swings her sword. In the midst of a horrific battlefield, where corpses litter the entire landscape—

Lady Wolnyeo, the image will be next.

Qing was hidden behind a dense trajectory of black smoke.

Because it was just a sword technique used to blind the opponent.

For a brief moment, Qing, who had disappeared from sight, drew in all her energy from her dantian and took a deep breath.

A blue headdress that shines brilliantly with gold.

Suddenly, a fantasy comes to mind, as if beautiful arms were spread out to the left and right behind Qing.

She was covered in countless bracelets of five-colored splendid gold, coral, jade, emerald, and mother-of-pearl, to the point that her skin was invisible. This was an adornment that only the most noble woman in the three thousand worlds can wear.

The arms of the most noble person in the world slowly moved over Qing's head, leaving countless afterimages, and finally the left and right met in one place.

The number of those afterimages was one thousand, and the one thousand arms form a halo, emitting a brilliant light.

With a thousand hands, he comforts and caresses all living beings, and with a thousand eyes located on his palms, he does not turn away from living beings in the three thousand worlds.

The Buddha who looks down on the present world, the King of Righteous Law Tathagata, the most noble woman, Avalokitesvara Bodhisattva.

Tathagata's body, eight limbs, thousand-armed and thousand-eyed Tathagata.

Qing stretches out his head.

Doo-woong… … … !

The sound of a thousand temple bells ringing at once.

But it was never loud or noisy, it was just the sound of the temple bell that was a thousand times deeper, and it was the most peaceful melody in the world that echoes faintly as if embracing all of the world.

however.

The voice of the angry Buddha breaking the clear sound of Brahma.

Ohh …

A huge blood-red palm, a bloody one, rushed towards Qing.

The golden blue sword with a halo stretches out, and the two finally collide.

!!!!!!!!!!

A terrible roar, unprecedented in the world, that shook heaven and earth!

At the same time, a golden, blood-red light soars, filling the world with a dazzling flash.

In it, Qing suddenly spits out blood.

My dantian began to ache, and the excruciating pain felt as if all the energy and blood vessels leading to my left hand's center were being torn apart.

Miss, it's dazzling.

Qing covered my eyes, squinted, and stared intently beyond the light.

… … Did you get it? Huh, what am I thinking now?

Qing realized that she had recited the mantra of resurrection without realizing it.

At the same time, I realized that this was just a thought that popped up automatically.

But it wasn't called the resurrection mantra for nothing.

My eyes met with Na-Cheok's, who was frowning in a similar posture to Qing.

Both of their expressions suddenly crumpled.

'You're a tough old man, can you handle it?'

'Crazy bitch, you can stand this?'

Even their thoughts were the same.

The moment Qing hid his body behind the dense steel using the technique of Insangjeongheo, Na Cheok also prepared the best move he could without delay.

The old man's forehead was red and wet, as if he had suffered a considerable shock from the collision with the other god.

'Tough old man.' 'Poisonous bitch.'

The two people were looking at each other with tired eyes.

That moment.

Qing's eyes widened and she suddenly raised her voice and shouted.

"Amukhaprap! Now! Do it now!"