\chapter{Chaka Salt Lake Murder Case (4)}

It's not difficult to start a fire.

A salt kiln was originally a device for boiling salt water. It was a structure that places a heavy kiln on top of bricks and lights a high fire underneath.

So, there was no need to search for the remaining fuel in the first place, and if you just light a spark, it will immediately burst into flames.

"Don't light a fire, they-"

"It's okay. Do you think I'm just some expert? You're freezing to death right now, and we'll leave before those bastards get here. Look at your little sister. She's already turning pale."

"It won't work……"

The little boy's voice trailed off, wondering if bringing up his younger brother was the right answer.

I change the wick again, open the still-sparkling incense burner, and light it. Then I light another one next to it, and then I light the two on the opposite side. The heat spreads out in all directions, and in an instant, the temperature rises to a feverish level.

"Where do you keep the dried manure?"

"Oh, that's me-"

"Oh, Jiji, Jiji. Kids don't touch Jiji. Why don't they just use their mouths and fingers? Hmm, over there? Watch the kids over here."

In the first place, would the primitive ancient Zhongyuan' still underdeveloped production facilities have such a complex structure?

Rather, these facilities have a simpler structure, and places that require manpower were usually stored with large doors in easily accessible places, and materials that were frequently used were stored with large doors next to where they were used.

As soon as you enter the dry storage room, a pungent smell fills your nostrils.

The slurry was black, so it seems like the slurry's intestinal health wasn't very good… … No, sniff sniff, it was kneaded with coal. Somehow, even though there wasn't much left, the heat was quite strong.

Thanks to this, the salt room, which was quite spacious, quickly becomes warm and smoky.

Qing takes a quick look at the unique and oddly constructed ventilation shaft through which smoke escapes.

Did you make the roof slant?

The fact that the smoke escaped meant that it was visible from outside.

"Xiao-mei? Are you here?"

So, the group also had no choice but to quickly see the smoke and come running.

The younger of the siblings was Cha Ma-kyung, fifteen years old, and the older one was Chana-mo, thirteen years old.

Chama-kyung was a small kid for a fifteen-year-old, and CHenano was very tall for a thirteen-year-old. I think that if he does well, he could be taller than me.

It was not a common name for a long-legged person.

According to the explanation of the village resident, Bengshi, the original Seojang people did not have a surname.

Of course, the high ranking monk leaders were an exception.

Instead, write two names.

Amukhaprap was a prime example.

The name of Amukhaprap was not Amukhaprap.

Amuk and Haprap, two names!

However, since the people in the West were also people, wouldn't it have been inconvenient and cumbersome to call someone by two names, one with two syllables if it's short and one with four syllables if it's long?

So, if we take the example of Amuk and Haprap, you can call it Amuk or Haprap.

However, the most popular way was to call them by just the first letters of their names.

In the case of Amukhabrap, the most common title was said to be Ahab.

However, it was said that the barbarians of that western region keep this tradition, while the Jang people living in Qinghai take one surname and make it into a Zhongyuan style.

Well, the administration of Zhongyuan was based on surnames and given names.

This was the case with the Cha siblings.

It was just a case of our village being called Chajapchon? Then we should just use the Cha surname.

As I listen to the explanation, the words between Amukhaprap and that steel nipple come to mind.

Didn't you shout that our chief's children were talking and thinking like those Zhongyuan guys?

But if you think about it for a moment, it's funny.

If you're from Qinghai, aren't you just a person from Zhongyuan?

I don't know about the history, but from what I've seen from time to time, there doesn't seem to be any oppression or anything like the people of Zhongyuan in my hometown, like the lower-class humans.

Just looking at the land of Xining, there were many Muslims, Buddhists, and even Taoists who seek communal sects, and they were all left to their own devices.

Surprisingly, throughout history, the imperial family has not particularly discriminated against barbarians.

To be precise, it was close to treating barbarians and Han Chinese very harshly, without discrimination, as if they were slaves who could be squeezed out of one's possessions and done with as one pleases.

Even the Hongmogwi (white people) and Haegwi (black people) were quite peculiar barbarians, but they were not specifically rejected, so if you look for them, you can find them secretly living here and there, one or two at a time.

Rather, there were quite a few people working as interpreters because of the preferential treatment for Hongmo-gwi, and Hae-gwi was rumored to be a very good fighter, so he was on the reserve force's military register.

Of course, Qing (direct lineage of the imperial family, Princess Sohal) does not recognize herself as a person from Zhongyuan, and considers herself an outsider, and has even less interest in the history of the Zhongyuan.

So, isn't that just how it is? I just say that's how it was because that's what I've seen with my own eyes.

The barbarians' position may be different, though.

Anyway, Chama-kyung explains my situation in perfect Chinese.

"At first I thought they were lamas. But Yappa said we had to hide."

The Qing's ingenious language understanding system tells her that yappa means father in Xizang language.

\textit{Well, how the hell does this translation work? I really don't understand the mechanics.}

"So I hid, but the traitor was yelling, ‘Where did you hide him?' and there was a scream…"

The child's words were trembling and watery.

My younger sister holding my brother's hand tightly.

Even though Cha Ma-gyeong's eyes were bloodshot, it was clear that she was holding back tears.

"So, I went out at night, and it was dark."

When the lamas came to the village, the villagers welcomed them politely and made offerings.

However, the faces of the lamas who had been listening to the names of the residents, saying that they would pray for their virtue, gradually became distorted like evil spirits, and they suddenly shouted at them, calling them soul-seller and demanding that they hand over the traitors immediately.

The father of the siblings realized the danger and immediately pushed the children into the salt kiln.

Terrible noises echo through the siblings trapped in the dark, initially warm salt kiln.

The furnace was getting colder, and the siblings had to survive on the leather and food their father had provided for them for a full day.

When Cha Ma-kyung went out at night to look for her father, there were dead bodies everywhere.

However, the boy's courage was amazing, and he dragged the villagers' corpses outside in the cold night and carefully placed them there.

"The birds don't come to the village. They keep chasing them away, saying they spoil the salt. But if the birds don't eat the body, the deceased will have to wander the afterlife without guidance. That's what Yappa said when Yomma passed away."

Yomma means mother in the words of Xizang.

No matter where you go in the world, mom and dad all have similar pronunciations, so the first thing a child says when he or she was born and the pronunciation he or she uses to call him or her was the same everywhere.

So, the villagers' bodies were moved outside for burial.

But on this winter night, a bitterly cold night, a child, unusually short and small in stature, dragged frozen corpses.

How cold, how hard, how difficult, how much fear must one have endured?

Fortunately, however, he said his father's body was not found.

The words, which were almost like sobbing, as he cried and said that he was relieved that he couldn't find his father.

It was a lie that was obvious not only to Qing but also to everyone else.

It was a lie for the sake of the younger sibling next to him.

A child who had to drag his father's body in that cold, in that running stamina, in that fear.

Qing's heart hardened.

Why on earth? Those people who claim to be for the Toban, Seojang, and Jangjok.

"Truly, wonderful, how……! Oh my, ugh, ugh, huh. How, the Lord, is this."

Dew Jade Sword Bengshi was shedding tears, but even in the midst of that, he does not spare praise in a choked voice.

Qing stroked the back of the child's head, holding back the endless anger and the comfort that was hiding within him.

After feeding them a hearty meal of nutritious porridge made with the remaining food in the village, the siblings, who must have been tired from hiding in the pot, dozed off and soon fell into a deep sleep.

This was the boy that the men of Zhongyuan dream of, and who shamelessly fell asleep after cutting the thigh of the princess of the royal family.

The younger brother was lying down in Jian Buxi's arms, breathing deeply and wheezing.

In fact, I wanted to let my younger brother sleep, but for some reason, Cha Ma-kyung desperately tried to stop my younger brother from approaching me as if he were suffering from a plague.

He was so close to me that I couldn't even reach out to CHenano, so he kept watch over me, and I ended up having the honor of lying down and cutting Qing's thigh.

"It's the Xizang's bastards again, right?"

"Tsk, I've already seen that trick, but it's going too far. It's a village, but to mess with the salt farm."

What Paengdaesan said was not that the salt farm was more important than the villagers.

Salt was a resource managed by the state, which means that touching the salt room was tantamount to directly raising an issue with the government.

However, the group had already heard some crazy things about Tibet and other places.

So, these kids really made up their minds, and the seriousness of it doubles.

The Bengshi's expression was filled with sadness.

"It seems this was not an ordinary matter. We don't know where the lamas have gone, and they might do something like this again. We must report this immediately to the main temple to protect the people."

That's true, though.

But it took two days to get there, and then two more to get back. And then the sect showed up and said, "We have to go!" and then they all rushed out, saying, "Let's go right away!" Was it something like that?

Even if the devil hits and comes out right away, it will take at least four days.

"Those lamas will continue to wreak havoc in the meantime. Bung So-hyeop, was there a nearby village? Where they might have headed? Since we didn't encounter them on our way, we doubt they'd have missed us."

"If they were from the west, they would have definitely stormed through the western road, so if we assume they were taking the road, they must have headed north."

He glances around at his friends.

Since they have already been through a lot of hardship, they were not the ones who would not understand that look in my eyes.

"No. It's dangerous."

"This dog has no right to speak. How can you, the weakest of the weak, dare to bring up danger? This dog was dangerous everywhere in the world, not just there."

"This was too much."

"Okay. Um, would you like to take the kids and return to Kunlun first? We need to deliver some news. Um, the kids…"

"He is truly a boy of excellent heart. He deserves to be embraced by Kunlun. Furthermore, since we cannot separate from the natural order, I will ask that the girl be brought in as well."

"Ah. That's really fortunate."

"Young Lady Ximen, are you planning to chase after those lamas?"

"Yes. I think that's the right thing to do."

"Well, then I won't bother to stop you. I respect that conviction and wish you good luck."

I don't know if it's a conviction or what, but I can't just let those bastards breathe freely.

No, it shouldn't be alive and breathing.

Whether it's heaven's will or not, I'm so pissed off that it won't work.

I won't kill you nicely.

Isn't the thing I like most about coming to Zhongyuan the fact that I can beat these little bastards to death without any problems, and even receive praise for it?

And perhaps, if Master and Teacher had seen this right away, they would have done the same.

So the disciple cannot escape from here.

Even if you become a strange disciple, you must not become a shameful disciple.

And in fact, it's not like Yi-mei, Sani, and I can even compare to each other.

Here, um. Yeah. Well. That's why.

Even if I tell you to go anyway, you'll never go.

Qing carefully moves Chama-gyeong's head onto the fur below and stands up.

We don't know where those lamas might be wreaking havoc again, so we should wait until morning to avoid creating more victims.

As it was nearing the end of the year, the moon was waning, but fortunately the sky was clear and bright, so the night vision was not so dark that it was difficult for the experts to see.

So, if you want to go, it makes sense to start right now.
