\chapter{Chaka Salt Lake Murder Case (8)}

It wasn't difficult to follow the lamas.

The Lama monks had no idols, no famous people or great figures.

Even on the way, people I met would kneel down on the road and bow down to me, so I thought, how unusual was it to even ask for a single blessing?

So, all I could do was watch the uproar unfold from afar.

By the way, Xue-i-ri tilted her head.

I thought it looked familiar, and then the happy faces of the employees at Xuega Sanghoe offering snacks to Qing came to mind.

In contrast, the lamas were completely unresponsive.

He wanders around the city, asking those who pray for him what to say.

There was no need to wonder what he was asking.

"Excuse me. What did the monk say?"

"They asked if there was a monk who had visited before. I heard he was badly injured and in critical condition. I hope he's okay…"

"Oh, like that. Like that."

Of course, there was a problem of reputation if a traitor to the sect appeared openly, and even if Amukhaprap was hiding somewhere and recovering from his injuries, wouldn't he be able to tell right away since the monks who hid him were probably the same ones?

It seems like you're being very emotional.

Still, they were petty people who didn't have the guts to touch the city.

So, Qing was chasing him from afar.

The lamas who were stroking the head of the long-legged man and praying suddenly stopped moving.

They look at each other, their expressions become very serious, their lips quiver, and they grab one of the long-legged men and seem to be questioning him on various matters.

And then he walks briskly and hurriedly into the alley.

What urgent matter could there be for a lama?

"Let's go. I think the fish cake man got caught."

The Qing party also increases its speed.

As I pretended to pass by and looked into the narrow alley, luckily I caught sight of some lamas turning left at the end.

The group of Qings unnaturally turned, and with even more unnatural sounds like "Oh, right, here it is," they dug into the alley as if they were passing by without noticing.

He walks away quietly, making no sound, and sends the basic hand signal of the Qing Wulin Alliance.

Quickly. Quietly. In front of here. Right. It's there. Left. Aim for the head. Valid.

At the end, pretend to go right and look left naturally.

At the end of that fairly long alley, a minor problem arose.

Hmm. It wasn't a fork in the road, it was just a single road that turned left…

This was the root of the Qing, the weakness of the Korean people.

In the Qing Dynasty, the city was built according to a pre-planned plan, so no matter which way you went, you just had to turn and turn and turn until the road eventually opened up without any obstructions.

So if you go this way, it will be faster, and if you do that, you can go really fast.

but.

This was actually a rare case.

In a city that has been built and expanded haphazardly, the alleyways have no context, so they turn at will, end abruptly in the middle, or go around in circles and come out right next to where they came in.

Because the assumption that if you go this way, you will come out this way was completely wrong.

So the group looks at Qing.

Qing sends a signal again.

It's not weird. Liar. Gil. Go.

Let's just pretend not to know and follow the road normally.

And then Qing suddenly opened his mouth.

"No, where on earth was your uncle's house?"

At that, Jian Buxi tilted her head. How cute.

Xue-i-ri tilts her head. She's so cute.

But the reaction was explosive.

Even if Yi-mei's brain was pure, what's wrong with Gunyeong? What was her thinking?

Fortunately, Peng Daesan Mountain matches the rhythm.

"Don't rush me too much. My uncle was moving, and it's not even my neighborhood."

The mountain, after all!

Still, it's the end of the intellectuals.

You're acting like the most stupid intellect!

"Is this the right way to go? It's getting creepier and creepier. You're not taking me somewhere weird, were you? If it's not this alley like before, I'll really not let you go."

"What if you don't leave me alone? If you won't go, I'll live here. I'll go to my uncle's house."

"No, that here?"

Just pretend to be someone passing by.

That's also pretending to get lost because you don't know the way.

About ten steps ahead, there was a wall again.

Looking closely, it was connected to the left, so it means that it was a single road that turns to the right.

So, without any need to wander, let's turn the corner and go-

The group stopped.

Well, wouldn't three lamas be waiting in a row, blocking the alley?

"What kind of people were they?"

"Huh? Us? You might ask, 'What kind of people were we?'"

"Don't pretend you didn't notice. I saw you in the square, eating like a pig. You piled up so many bowls, and you thought I wouldn't notice if you pretended not to notice? Why were you following the monk's ceremonies?"

Xue-i-ri and Paengdae-san look at Qing.

What was that slanted eye shape? Why were you looking at me with that expression?

"No, what, pig? No, how about eating a little more? Ha, that's funny. Monk, do you know me? Why were we picking a fight from the start? Monk, what kind of era was this? Kids these days don't cower like they did in Gramps's time when adults say this guy."

The lama's eyebrows twitched greatly.

But the expression becomes slightly ambiguous.

"I'm the daughter of a noble family, and I've also learned martial arts. Why would I pick a fight with a man with a sword?"

The lamas exchange glances with each other.

I know that bitch was a real rascal, right? That's not the typical reaction of someone caught being followed.

But they were clearly the ones who were glancing around the square and pretending not to notice.

Of course, if they were people from Zhongyuan, it might seem strange to see them preaching.

Self-pity.

That was the moment.

At the corner of the alleyway we passed, three other lamas appear.

Two men holding long clubs, one bare-handed.

Qing pretended to be surprised and took a step back.

"What, what was it? Do you think our house was just another house? The Xuega Sanghoe has a really tight grip on Hubei Province. If you harm me, my old man—no, dad, no, father—will not let you off easy. I really warned you. Hey, Cheolsu, were you going to just sit back and watch? I heard you learned martial arts from the General."

"Hmm."

Then, Paengdaesan blocks Qing's path and grabs the handle of his sword.

The lamas' expressions become more ambiguous.

It's like I'm a fool living in a foreign land.

But why was there a foreigner in this closed city?

Then, Qing completely changes direction and looks across the alley, making a fuss.

"What, you, don't come, don't come? Why, what, what, what was it? Hey, Gunyoung, stop me, I said stop me."

Then he grabbed the woman behind him and pushed her towards me.

Since the suspicious guys were chasing after them, another group decided to capture the rear, but if you don't know the situation, it seems like it would be quite threatening.

The lamas were further strengthened by this.

I guess they're just a bunch of idiots?

Looking at the brat who has no iron fist, it definitely seems like he has a backing.

The oldest lama in the front speaks in a soft voice.

"Oh, it was just a brief misunderstanding. I didn't mean any harm."

It was actually a call to inform the rear guard, not the Qing party.

This isn't tailing, so don't touch it.

"Really? But why were you carrying a weapon? Then put the weapon away first."

"Lions, put away your weapons!"

The lamas blocking the back alley then lifted the long staff they had been holding tightly with both hands and placed it on the ground with one hand like a walking stick.

It was almost Jangbong's only advantage.

It doesn't look like a weapon when you just hold it in your hand.

Of course, Jang Bong's shortcomings were also like that.

The power doesn't seem like a weapon.

"I have some business to attend to here, so I'm sorry to bother you, but could you please come back an hour later?"

"Joe, all right. Then, please make way. Or should the monks pass first?"

"[The lions, step back and continue your search.] It seems the master was a bit sensitive. For now, guide those bastards, no, those people, outside."

"[Yes.] Dear patrons, come this way."

A monk from a back alley answers in his awkward Chinese dialect.

Still, it was much more of a Zhongyuan word than Amukhaprap.

What the heck? Where on earth did you learn that Zhongyuan dialect to be like that? Even if you learned it from a book, it wouldn't be that good.

But a new question has arisen.

Anyway, the Qing party quietly turns back down the alley.

The shape of a blue hand secretly drawing behind one's back.

Here, there's a surprise attack. Me, center. Mountain on the left, Heimae on the right. No, kill. Legs valid. Then escape.

What can you do? If you've been fooled, you deserve to be punished.

Qing's acting skills were usually poor, so he doesn't want to fool good people.

However, if those were not human children, then it would be a completely different thing to kill those children, a killer's intelligence, a killer's ultimate skill.

The Qing party passes by, sticking close to the wall and watching closely.

Of course, Xue-i-ri didn't have the ability to control her expression at times like this, but in any case, it was natural for her to look nervous now.

And so the lamas stepped aside and the moment the two passed by!

Qing moonlight sword, drawn out in an instant, shot out at lightning speed.

A fleeting illusion.

A beautiful woman, so noble that her charms flow out of her, was walking gracefully under the moonlight. Her figure was so elegant that it flows out of her, huh, Master?

Then, suddenly, a group of obviously bad guys block the Master's path.

He opens his mouth and says something, but it's obvious that he's blocking the woman's path in the middle of the night and saying something mean.

Well, of all things. Isn't it strange that a stunning beauty would be wandering around alone in the middle of the night?

Or maybe it's the courage to try, even though it's strange.

Even as the men approached, the master stood still, with indifferent eyes.

But as expected, the moment the man approached, he fell asleep in an instant!

A great swordsmanship, a surprise attack without even a hint of warning.

Ximen Surinryu Divine Maiden Sword, the second of the two.

A woman can protect herself.

Qing sword was stuck in the lama's lap.

The speed of the girl in the image, Ximen Surin, was far superior to that of the girl in the image, but at that time, Ximen Surin was not a master of Hwagyeong.

However, the technique of the sword was useless except for surprise attacks, and was a despicable technique used only for surprise attacks.

In fact, no matter how strong the swordsmanship is, it was not even half the power of a normal sword swing.

It's common sense that the bigger the weapon and movement, the stronger the power.

So the significance of the art of footwork lies in how one can launch an unexpected, fast, and powerful attack from an ordinary stance.

In that sense, this herbivore isn't really a great technique.

"Ugh!"

The blade that pierced his knee with Qing's conviction slipped outwards, and he retrieved the sword from between his legs and continued his attack by rising upwards.

"Ahhhh!!!"

When the knee was cut off to the extent of an arm, people swallow their screams, but when the daring procedure of lengthening the leg by making an incision of about an inch in the shin was performed, there was an enthusiastic cheer.

And then, a beat later, screams erupt from both the left and right.

"Ahh!" "Ahhhh!"

Well, that's why they're called sewers.

Even surprise attacks were slow.

Well, they say that even the lower classes were slow to fall, so a surprise attack would be foolish.

"Hee-mae, come here! This way!"

"huh!"

Qing steps on a stone wall and climbs onto a brick house, and the group follows Qing onto the roof of someone else's house, disappearing without a trace.

Oh my, the screams were exploding!

From around the corner of the alley, the lamas rush in urgently.

But it was already too late, so they disappeared, either sinking to the ground or rising to the sky.

And on the floor, three lamas lay sprawled, screaming in agony.

One of them was dangling with about two inches of knee left, and the blood flowing out of his groin, which he was holding tightly with both hands, was a terrible sight.

One had a piece of flesh on the outer thigh ripped off, exposing a reddish cross-section.

The remaining ones had clearly visible footprints, with their elbows bent in the opposite direction and their ankles crushed.

"[Maha, Pasu, look after your disciples!]"

That was the reason why Qing didn't kill him and instead aimed for his legs.

It's a shame that he's dead, but we can just leave him alone. (It's also a shame to kill him comfortably.)

Those with injured arms, torso, or head can walk away on their own.

But if you hurt your leg, your colleagues have to take care of you and carry you.

The old lama also recognized the malicious look at a glance.

"[These damned bastards! How dare you! I will never forgive you!]"

An old lama runs out of the alley, groaning.