\chapter{Chaka Salt Lake Murder Case (14)}

The courtesy sign has reappeared.

These were fake monks who pretend to be monks and have a vile sexual desire for corpses.

So, these were the demons who were currently known to have annihilated three villages, including Chajapchon, raped them, and then ate their corpses.

Don't throw hard objects like rocks. Soft waste was fine. It's even better if you throw rotten food. Be careful around the mouth, as it can bite, etc…

It was a neat and powerful piece of writing that ended with the words, "Let's create a mature viewing culture to establish justice through the words of the wicked."

Unfortunately, among the cities in Zhongyuan, Cheonjun was the most rural and remote.

Most of the residents there were Jangjok.

So I didn't really know how excellent the handwriting was.

In fact, it was more important to be wary of having your writing stolen than of throwing stones or throwing a stick, but country people don't know that.

Instead, the charges were written in neat handwriting at a glance, which gave him more credibility.

The Jangjok people spit and swear.

"Stuck in a corpse? You dirty, filthy bastards."

"And yet you pretend to be a monk? Aren't you afraid of divine punishment? You're worse than beasts!"

I did add a little spice to the charges.

Rather than talking about how Toban was a pure general and such, it was much clearer to say that he committed massacre because he liked time.

It's easy for viewers to understand that he's a guy who deserves to die.

Qing has no intention of turning these bastards into martyrs who dream of national liberation.

They say that if you're not careful, you'll end up in trash in no time.

In an instant, they were necrophiliacs who became cannibals.

If I could make a sound, I would protest, but that was impossible.

Looking at the tears streaming down her face, stained with resentment and anger, Qing couldn't understand at all.

Even if their plan had succeeded, weren't eight out of ten of the city's residents traitors who needed to be killed?

What could be so unfair about these malicious murderers that they were shedding hot tears?

Should I kill the residents without worrying about what they think?

Hmm. That's really cool.

Qing turns his gaze and looks at the Strange Monk.

The pale complexion was not ordinary.

It was a truly astonishing sight, proving that although originally skin was stretched over the bones, it could be made even thinner.

Well, if your arm was cut off, it doesn't just heal and be over.

Of course, the fever was boiling and the body was weak, so just sitting there pretending to be calm was a sign of great patience.

"So, what happened?"

"My greatness was not a concern for one arm."

"No, the arm was fine. The lamas must have eaten it, right? It's not like he suddenly lost weight because he was heavy, and he didn't pay tuition to attain enlightenment, right?"

By the way, the person who paid his arm as tuition to attain enlightenment was called Hyega.

He was a disciple of the famous Master Bodhidharma, and Bodhidharma was satisfied with his generous tuition and eventually gave him enlightenment in one sitting.

"I will return to the Arabdaltaekbulsin Temple. Originally, it was for the sake of our Bloody Thunder Temple's leader, so I will personally lead the way and set an example. However, there has always been a foolish monk. He contacted the Podalap's Dangjung and planned to rule them. That's right. Let me first explain Podalap. Currently, there were two main types of Buddhas…"

Amukhaprap explains.

But the way of speaking was the way of speaking, and it was not easy to understand because it crosses the past and present.

As I was going, yes, it was originally like this, so I did this, but there was a reason why it was like this in the past, and there was another reason for this reason, so it was a flow of consciousness.

The current structure was that of a theocratic, religious leader ruling the region.

Originally, there was a dynasty, but recently, the head of a Buddhist sect called Hwanggyo, with the help of foreign powers, overthrew the dynasty and ascended to the throne as the religious leader and king of the West.

What about Zhongyuan?

It was said that after the Shaolin Temple defeated the imperial family with the help of barbarians, the abbot ascended to the throne.

"Those ugly bastards aren't monks. They're just using the Buddha as a means to gain power! After becoming king, the country becomes unstable, and the only means was Tibet!"

It was not a surprising fact.

Since ancient times, when a country was internally unstable, it tended to wage war and project its power externally.

Countless examples throughout history have proven the excellent effectiveness of war as a method of swaying public sentiment in the name of patriotism and of reducing local armies to enhance royal authority.

After all, rulers don't shed blood.

Blood was shed by the people, and the rulers just enjoy themselves and when that doesn't work out, they just declare defeat and kneel down.

So, the fact that Amukhaprap was spitting out fire was a condemnation of this.

"This isn't a Buddhist idea. It's ugly! The idea that mothers don't exist! Saving sentient beings was the duty of a monk! But the monks who should be removing genitals and putting them in their mouths were instead attempting to push them into hell! Ugly! Filthy! My nose was numb, so I can't even smell anything!"

"Huh. Fish cake? You lost not only your arms, but your sense of smell as well? Wow. They say if you can't smell, nothing tastes good."

"You brave soul, you still have nothing in your head! As you yourself say, the true meaning of this terrible stench was this!"

Meanwhile, the number of Arab Dal-Taek-Bul-Shin-Sa and Blood Thunder-Eum-Sa who were also obsessed with this nonsense and war games was increasing one by one.

"The master and I took the wind out of those kids who were having a blast. A club was a great tool of discipline. Beating the wind that's been building up will make it go away again. That's what I thought. However, since the great master's parents were absent, I didn't realize that the cause was the unfilial son who beat them to death."

At this time, a map of Jangbo flew towards the Blood Thunder Demon Temple, and it was a map with the location of the Absorption Great Law Divine Art written on it.

It was said that poison and medicine were the same thing, but their uses differ depending on how they were used.

Even if there were those who possess the magic called Saljungsal, if they were prospective Buddhas with a pure mind, they will rather become fertilizer for the world.

Of course, if we fall to those rotten Zhongyuan bastards from the very beginning, it will be a great disaster for the world.

"Thus, the great One Himself sought to recover the divine power. This was a sacred act for the world, an astonishing act of compassion, a bravery that would astonish even the Buddha."

"I guess I'll have to ask Buddha about that."

Anyway.

Amukhaprap set out on a journey to keep the Absorbing Magical Arts away from the evil Zhongyuan people and to enter a pure Buddhist temple to use it for the good of the world.

In the end, I had to return empty-handed.

And when he finally arrived at the Blood Thunder Temple, almost half of the familiar faces of the Arabdaltaek Buddhist priests had disappeared.

And the first-ever chiefs were swarming around, and the war-mongers who had been living in vain were running wild in the repentance hall.

It turns out that Bangjangseung, who was thought to be a devout Buddhist until now, was actually a lackey of Podalrap Palace.

As soon as Amukhaprap left his post, he revealed his true colors that he had been hiding until then, and a bloody purge was carried out immediately.

It was a brutal death for moderate monks, true Buddhists who were trying to save the poor through illegal means.

"You \#\#\#\#s who will \#\#\#\#\#\#! How can you be such crazy devils in human skin! \#\# \#\#\#\# \#\#\#\# \#\#\#\#\#\# \#\#\# \#\# \#\#\#\# \#\# \#\#\# \#\# \#\#\# \#\# \#\#\# \#\#\# \#\#!"

The anger of the Amukhapalap was proven by the thick, endless profanity of the prologue.

And finally, the blade reached Amukhaprap.

Just being alive now was a gruesome survival skill, and wouldn't it be a cheap price to pay for one arm?

Suddenly, a dark shadow falls over Amukhaprap's face.

"You fool, unworthy of your own anger. You were deceived by your own vile master, harming countless innocent people. You deserve to go to hell. Yes, you deserve to go to hell."

"Hmm."

Qing let out a groan of embarrassment.

Since he was sent to punish criminals who had fled to Zhongyuan under the orders of the chief priest, wasn't the title of Amukhaprap the Acting Chief Priest?

It means that he has the qualifications to go to Zhongyuan and represent the Blood Thunderer to punish criminals.

What was the sound that came back when I yelled at the room leader and gave him a stern reprimand?

Then what about the innocent people you killed? It was a cold sneer, asking if you were qualified to discuss compassion with Buddha.

"I will go to hell myself. But I will never go alone. I must accompany those vile demons. That's why I am still alive."

And then he nodded to Qing.

"Thank you for your brave help. With this, the true master of the Blood Thunder Sound Temple, the abbot's son, exists alone. I, the Blood Thunder Sound Temple, burned down, leaving not a single cornerstone untouched. This was a meritorious deed for the world. However, I am unworthy, so I will yield the credit to you, the brave soul."

"Is it transferable like that?"

"The Blood Thunder Demon, the den of evil, so I can no longer ask you, the valiant one, to return to me. Instead, I bestow upon you a wonderful great Divine Art."

I've heard that before, but this time, instead of a palm, two books were flying towards me.

As Qing accepted it in a fluster, a martial arts window sparkles in the corner of her vision, causing a ruckus as it told her to open it.

Qing ignored it for now.

"Huh? Are you giving it to me?"

"I also bestow upon you the remarkable study of Mansangyeoiltaeilhoegi. However, I will leave it to you for a moment. Instead, you, the valiant one, were qualified to master this study on your own. You, the valiant one, still have a long life ahead of you. In the distant future, when the excellent monks of Hyeolroeumsa Temple, now reduced to ashes, rebuild it and establish true Buddhism, I will request that you return it to me."

Hey, Qing, Hmm.

"You sound like you're about to die."

"You brave soul, you still have something stuck in your ear. I already said I'm going to hell, but I plan to find a companion."

It seems that he planned to attack the Blood Thunder Temple alon, entrusting the Secret Manual will be returned to the proper Buddhist later.

Qing shook her head at him.

"If I go now, my body's not even healthy, what's the point of going to hell? I've always tried to do everything on my own, but now I realize that even the most insignificant person feels better when someone helps them."

In the trivial part, Qing's gaze turns very naturally to Xue-i-ri as if it were a given.

A small scratch appears between Xue-i-ri's eyebrows.

To Qing, an expert in analyzing Xue-i's facial expressions, it was a very unfair expression.

Qing'er Heng, if you feel wronged, you should at least take a picture of the climax.

This was all a call to action to get well soon.

If you keep nagging, you'll reach the peak even if it's dirty, right?

It was also a method whose effectiveness has already been proven through mountain and black rain.

The expression on his face brightened.

"Oh, you brave one. You're helping to destroy that ugly Blood Thunder Demon? You brave one, you're no longer an honored member of U-Tsang. Nor were you Han Chinese. You're a proud member of the U-Tsang. This is a tremendous honor that will be passed down to future generations."

Qing (direct lineage of the imperial family) actually didn't know whether she was Han, Zhuang, or Daldan, and she didn't really want to know.

What makes a person change depending on their bloodline?

"Will it be just the two of us? And with all these unknown faces, how can you be sure there's a master among them?"

"You're not helping? You're deceiving myself?"

"The Elders of Alliance were planning to come to help. They're already trying to stop Xizang's invasion, so why don't we just tell them?"

Even without that, all the elders of the Jeongpa area should gather together. It's after the person left.

Then why would we fight and risk our precious lives?
