\chapter{Chaka Salt Lake Murder Case (10)}

Pang Dae-san understood the role he had to play among these idiots, these blind lackeys who would just raise their hand whenever Qing asked them to do something.

Otherwise, they would go around doing embarrassing or dangerous things that should not be shown to others, let alone rumored, as if it were a normal part of their daily lives.

If I had to say, I would say that Peng Daesan was also a common sense of the Ban-geom-ssang-do-hoe.

Of course, he was not as blind a servant as Peng Daesan thinks.

The only truly blind servant was my younger brother, Jian Buxi, who does whatever he wants, but he was not a member of the Half-Geom Ssangdohoe.

There was always at least one agenda item that everyone opposes or tries to block.

Xue-i-ri was sensitive to Qing's safety, so she always puts safety first and puts the brakes on dangerous things.

Tang Lan-ah originally had a cruel nature, so in this respect, he would think that it would be better to use poison, but he would try to maintain his dignity by eating it in front of others.

Nan-gong Shencai was also crazy about swords, but if this situation had been like this, he would have immediately opposed it.

Gong Sun-Yaoyi was a very strict person when it came to honor, such as meanness and trickery, and he had no chance to hang out with her.

Of course, if Murong Zhuxi were a villain, she would be able to act as a puppet because her eyes would be spinning.

"I know these guys were scum, deserving of a hundred deaths. Even death was a luxury, so I don't sympathize with your desire to live and suffer for as long as possible, but I can understand."

Pyeongdae Mountain was rising.

"But this time, you've gone too far. What about your reputation? Well, I won't listen to you complaining about reputation anyway, so speak your own way. It's human nature to feel pity for the weak. If you treat them like that, even if they were the scum of the earth, there will be those who defend you, questioning whether such a heinous crime was truly justifiable."

Qing'er hehe. He lets out a laugh typical of someone who has nothing to say.

"No, I know that much, don't you think? It's not something I'd show to anyone. But this time, there's nothing I can do. These guys were part of the fish cake uncle's sect, right?"

Qingdo was aware that it was not something he should do in front of others.

It was a very surprising fact.

However, Qing had already confirmed some of the martial arts of the Blood Thunder Demon Master instead of the Strange Monk or the Arab or something.

"That's because I haven't given them the space or distance to do that yet, but were these guys really that good? They can just slap you with their palms. They don't fly very fast, but they flicker and flicker, making it hard to see, and their trajectories were quite curved."

Destructive long-range means were dangerous.

To begin with, how lethal and dirty was an attack from a distance?

Isn't it a tacit agreement among humans that if an attack misses, even for a brief moment, they will show their weakness?

But if you keep your distance and just wave your palms from afar, and enemies who were compatible with you rush in, you will naturally see a really dirty sight.

Even Qing himself was the owner of the Tathagata Body, and he knows its usefulness well, having personally experienced it.

So, you need a shield.

If you carelessly wave your palm, you should remind them that it was fatal to the human shield and tie them up so they cannot use it.

What's so efficient about it in the first place?

Most martial arts weren't built with shields in mind, so even if the enemy hesitated, swinging a heavy weapon around wasn't exactly a good choice.

So I cut off the limbs and prepared them.

It's cumbersome and heavy as a shield decoration.

"Or was there another way?"

"No. That's enough."

It wasn't an objection to save face by saying it was Pyeongdae Mountain, so after hearing it, I quickly understood that it was true.

If it was to satisfy the boundless evil and sadism that Qing sometimes displays, I would have continued to oppose, but if it were for the safety of the group, what more could I not do?

It was only a moment before the monks of Blood Thunder Temple gathered together.

Of course, wouldn't the Geumgang Seungsa Napo and Cheoksin, who were leading the pursuit party, be screaming in rage?

The Vajrayana monks who had been conducting research on the city's elite also quickly joined their teacher, sensing that something serious had happened.

"[That's right!]" "[This, this was outrageous……!]"

The Vajrayana monks were furious when they heard the story.

Well, it's strange not to be angry.

"[But what about the empty-headed and ugly Buddha?]"

This was a Buddhist name written in the preface, and it makes you wonder if he would have given such a name unless he had a grudge against the person who gave him the precepts, or if he had a rather bad personality.

So, even though it was awkward to say the words, it was something I could not change now that I had abandoned the secular world and entered Nirvana.

Since the empty-headed and ugly Buddhas were nowhere to be seen, each of them took two disciples with them to go on an expedition, so wouldn't there be six?

Then, suddenly, Na-Cheok's face suddenly becomes distorted, like an evil spirit.

Those fucking bitches!

They were clearly targeting the precious reserve departments of the headquarters and tailing them, so they were clearly skilled at it.

As if I had done it several times before.

"[Damn it! We have to find them! Spread out, no, no! Vajrayana monks, follow me!]"

In front of these villains, of whom three out of four were using swords, and at least three were at the peak of their power, the only thing they can do was divide the number of people into small groups and offer them to them.

However, tracking the enemy was not difficult.

Because these crazy guys were running around destroying other people's walls, leaving the road to the public.

So the trail bypassed the central square and headed east towards the village, until it suddenly reached an alley where it came to a brick house with a gaping hole in the wall.

And among them, there were those who peacefully lit a fire and put a pot on it to boil porridge-

"[Profit! You guys!]"

"Oh, wait. In Zhongyuan, you should speak the Zhongyuan dialect. Do you want to use that nonsensical barbarian language? Hehe, no, but what do you say sounds like the roar of an animal? The chief said the barbarians were the children of monkeys. [Profit! Rerumruri!] Hehe, Gunyeong, how was it similar? I speak the chief language well, don't I?"

The faces of the lamas turn bright red, their veins rise, and their eyes narrow, and a genuine hatred blossoms in them.

"How dare you……!"

"Wait. Shut up?"

But, at Qing's one word, he kept his mouth shut.

The lamas who stick their heads out of the blankets, if they knew they had no limbs, they might give up.

Because it was a situation where I had my foot on top of the nose of a human shield with only its head sticking out.

"Want to see a watermelon shatter? Ah, you uncivilized barbarians don't know what a watermelon is? Want to see a barrel burst?"

"You guys-"

"Ssup. I know you're anxious to see your friends, but let's eat too. Oh, over there. Dangjung. Don't move. Squeak like a little rat. Don't move, keep your mouth shut. Wait quietly. Like a dog waiting for its owner."

It was an artistic sarcasm that even the Grand Elder of the Tang family acknowledges, a poisonous and intangible poison that scratches the very core.

"What do you want-"

"Miss, I told you to keep your mouth shut. were you deaf?"

Then, as if to show off, Qing pours the boiling porridge into the human shield's face.

Even though I was boiling hot and my mind was in disarray, the blanket was flapping violently.

"Oh, I was so surprised I knocked it over. What a shame."

It wasn't a look of pity at all, but rather, it seemed like he couldn't hold back his laughter, hehe, and eventually he let out a laugh.

Since you had a hearty breakfast, there's no need to pretend to eat a late meal.

It's just an act of art that makes the other person angry.

Qing was honestly still full.

So, Qing, who slowly emptied a bowl as a snack, burst into laughter at the vicious murderous intent that reached him.

Disqualified from being human, they were evil people who feel sorry for beasts, but why do they cherish their sect members and keep on living?

Maybe they were recalling the beautiful memories of massacring innocent civilians who did not even know martial arts with one heart.

"Why did you do that?"

"What were you talking about?"

"Chajapchon, and the small villages up here. The chief Buddha teaches us to kill the innocent and weak. That's why Tibet fell."

"You said your mouth was open-"

"Oh, you have a hostage here? Just answer my questions. Why did you go around killing all those innocent people?"

"that-"

Na-Cheok looks around with a start.

Even if it was a remote alley, once this commotion was made, there were bound to be people who came to watch.

In the primitive, ancient, and uncivilized Zhongyuan, where there was no entertainment, it was quite common to see the strange belief that one should watch the martial artists fight even if it meant getting killed by a spark.

"Ahem, I don't know what you're talking about."

"Really? Can you swear on Buddha?"

"Huh. Why do I have to swear an oath over such a ridiculous accusation?"

"If you're confident, you can just swear, right?"

Qing's eyes moved to the right and then to the left.

It means that there were eyes and ears watching.

"Huh. Yes. I swear to Buddha, I've never killed an innocent person!"

"Wow, this was hilarious. Everyone! These thugs here killed all the people of Chajapchon and ate their corpses! Do you know why? Because all the Jang people who speak Zhongyuan were bandits!"

"That's nonsense!"

"Then swear to me. I swear on the Buddha that I will not touch the people of Chajapchon."

His face was twitching.

But soon, he forced himself to smile.

"Yes, I swear by Buddha. Chajapchon? I didn't even touch it!"

"Since a monk betrayed the Buddha, he probably had no interest in Buddhism in the first place. So, how about this? Would you like to swear once more, on the honor of the Seojang people?"

"I already swore an oath, so why bother-"

"Oops, my hand again."

Qing scoops up a large ladleful and pours it over the human shield.

"Don't you understand the situation? Even if you're told to bark, you have to pretend to bark. So, what about your oath? On the honor of the Seojang people?"

"that."

As Na-Cheok hesitated, the other lamas' eyes also shook with anxiety.

If the lamas were like that, what about the onlookers? They forget to even breathe and just wait for an answer.

"I, I swear it. I swear on the honor of the Seojang people that it was a clear case of false accusation to have touched Chajapchon without even knowing it."

Qing sighed deeply.

Well, if it seems like you can avoid the crisis with just one word.

But I wondered if he had some kind of extremely strong belief that made him go around killing people.

Since you sold the Buddha, you were not a Buddhist disciple.

Since you sold the book, you were not a bookworm.

All that's left was just one ugly old man.

"Good. Since you swore an oath. Three. I'll only release the three precious ones. Okay. Choose. I'm curious to know which of the useless disciples you can discard."

It was a venomous way of speaking.

Because no matter who you choose, the rest will end up being useless people that can be thrown away.

But Na-Cheok has already sold out Buddha and sold out his people.

Now, there was no honor or justification, only an ugly purpose.

So, in case Qing's thoughts change, he quickly starts calling out names in order of rank.

"Doraek, Tunab, and-"

"No, how would I know if I told you your name? How many people were on the right?"

"Ahem. Second, third, seventh."

The expressions on the faces of the unnamed human shields were quite enjoyable to watch.

Despair, anger, sadness, self-loathing, etc… …

Oh, why aren't there any cameras in Jungwon? It's an expression I'd like to capture and keep forever.

Qing's lips were torn apart by an evil curse.

So, there were at least three hostages that were worth taking, and the rest were less important.

"Okay, I'll give it back to you. Please take it."

Qing lifts the blanket.

Ugh! The sound of people swallowing their breath loudly here and there.

Because the bald heads were a horrific sight, with only their torsos left, like fish in a fish market, without any limbs.

Everyone was shocked and frozen.

Qing blade dances.

A blade that skillfully cuts through the skin of the stomach.

The useless disciples who were not chosen by Na-Cheok fly towards the lama monk in a parabolic arc, their intestines dangling.

So there were one, two, three parabolas.

The lamas, startled and shocked, jumped up and grabbed the flying human shields.

Then he immediately lays him down on the ground, shoves his intestines inside, and begins to hastily take off his coat.

Well, since the stomach was upset, shouldn't we take care of it first?

One shield per person was enough, but that's why I went to the back alley to get three more.

A dead enemy only boosts the enemy's morale.

However, the injured enemy was no different from an ally, so they were a burden that forces the enemy to expend human resources.

Qing took up the human shield.

It's a thrilling pleasure that never gets old no matter how much you try to taunt your opponent with a pointless argument.

Because now was the time to use the sword, not the tongue.