\chapter{Chaka Salt Lake Murder Case (2)}

Qinghai Lake was a lush grassland stretching for 250 li by 250 li between long mountain ranges running east to west to the south.

In between, there were several waterways flowing into Qinghai Lake, so people settled in small villages around them, reclaiming large areas of farmland.

This was the reason why small villages could appear continuously south of Qinghai Lake. Qinghai Lake was salty and unfit for drinking water.

Munpa Village was one of those villages.

As the seasons were different, it was also the end of the points that can be reached by horseback in winter.

Because there was no facility to store hay to feed horses other than this.

"Oh, butt."

As Qing got off the horse and was rubbing her cold buttocks and swaying, Jian Buxi picked Qing up as if it were nothing special.

The breath rising from everyone's mouths was a sudden chill that added to the dampness characteristic of the water's edge.

Well, it's high ground to begin with.

The mountain slopes to the south were blocking the strong winds, so it's only this bad. On the other side, if you spit, it freezes before it hits or something.

And Lake Chajap was right across from it.

The question of whether to go see the tea house in this season was a direct reference to this cold weather.

It's worth seeing even in winter, but there's no reason to endure the cold at night to see it.

(It's just plain cold during the day.)

So I was thinking of just staying indoors.

"Miss Ximen, the moon was truly beautiful. The tranquil scenery of Qinghai Lake at night was truly breathtaking."

A clueless idiot looks at the night lake.

Then, Paengdaesan's eyebrows twitched again and again.

Well, I guess the kid really doesn't want to go since he's really cold.

But. Well. Since you're here now?

Qing was lying down and hugging, and if you look at him, he was the ultimate lazy bum, but in fact, he was a true walking enthusiast who enjoys walking around by himself.

It's just that he's seriously spread out when he can be lazy, but when someone tells him there's something to see, he's the type to jump up and say, "Oh, that's annoying. But let's go right now!"

"Who wants to go see the night lake!?"

"Do you want to see your sister-in-law? Should we go?" "Me too." "Tsk."

Even though they were both like that, it was Peng Daesan who clicks his tongue and sits down in front of the stove.

"What was it, San? Store?"

"Is there a place I can't go?"

"No, I'm really cold. Why don't you just rest inside? It's not mandatory, right? I'll just take a quick look and say, "Oh, that's it."

"Ladies, do you enjoy a drink? Taking a sip while watching the moon rise and fall over the water was truly the joy of life. This was life."

"Oh. Do you know Bung Daehyeop?"

"Didn't you say you were just going to take a quick look?"

"Just take a quick look, take a quick gulp, and come back."

"Hmm."

Anyway, it was Peng Daesan who grumbled while wearing a fur coat, then another fur coat on top of that, and then another coat on top of that.

What? were you going to work the night shift?

Anyway, the lake was pretty and the moon was pretty too.

It wasn't anything special, it was just a bright moonlit night with a cold wind blowing.

So, I'll put it in front of the night sea, blow on the bottle, and then come back and go to sleep.

For breakfast, I had a bowl of fish porridge with meat.

No, what was it? was it some kind of tasting event?

How can someone exert themselves after just one bowl of porridge? No, right? Just to taste it?

Of course, this was only a rumor, and Qingdo was fully aware of the stomach conditions of ordinary people.

It's because the stomach was small and the capacity was small.

Well, there were few people with such a great stomach as me.

Fortunately, there were few things that money can't do, so the villagers with nothing to do were rubbing their eyes and watching in amazement, wondering if it was a person or a ghost. It wasn't something they were secretly throwing away, it was something they were eating. Only then did the second day of the journey begin.

Thanks to the diligent horse riding the day before, the remaining distance was about 180 li.

It's not that far if you run to warm up your body a bit since it's cold outside.

Even in the hometown of Qing, if it's a long-distance running competition, they run one hundred and twenty-five li without stopping, so why can't a group of two peak runners, two super peak runners, and one expert run about three times further than that?

Besides, it's not like I have to run like a runner and get through in an hour and a half.

It's a good idea to take your time and move leisurely, with two o'clock in the morning and two o'clock in the afternoon.

The monk expressed regret, saying that he would only be looking at his feet and not seeing much if he ran during the tour, but he nodded obediently when told that he had to return before the Lunar New Year.

So, around 4 o'clock, the sun was starting to show its colors and was getting irritated.

Finally, my salt lake! My salt lake!

My salt lake… … .

Qing's eyebrows form a sad figure eight.

"Bung Daehyeop, what happened?"

"Oh. Isn't it truly magnificent?"

"No, it's not like I'm not a minister."

The salt flats stretch out wide, and the knee-high salt pillars stretch like icicles toward the sky, making for a spectacular sight.

This isn't what I expected.

Where did the fantastic scenery of the water flowing down the river, acting like a giant mirror, go?

With my superhuman eyesight, I occasionally see puddles of water, but the wind was blowing so fiercely that the sky was not visible, and only the water surface was noisy, leaving me in a state of confusion.

If this was the case, it's just a salt field, not a lake.

But for Qing, this disappointment was as useless as the physical recovery, and he was quick to use his power.

Oh, but still a little? I thought it would be pure white, but here and there it's bluish, so some places were more blue, some were less blue, and some were pure white, a random mix of scenery.

It looks like there's some kind of cosmic mold in there, but, well, it was worth coming to see it.

It doesn't seem like a landscape from this world.

"The salt was blue?"

"That's right."

Bengshi nodded as if it was natural.

His eyes narrow at him.

What? When you say, "Salt was blue," you usually mean, "Why was it blue? Did it get blue because it got hit?" and ask about its origin, right?

Here, a positive affirmation without any basis or end?

Well, the people of Borsa just enjoy the scenery, and people who live in the neighborhood don't really look for a reason when they see the local attractions, they just take it for granted.

However, the answer comes from an unexpected place.

"The original Qinghai salt was one of the most precious local specialties. It's not too salty, has a deep flavor, and was said to be completely free of bitterness. Apparently, that salt was Qing part."

"Oh. San. Did you hear that on the way here?"

"Huh. I heard it over your shoulder."

"Oh. Hmm. I've seen most of it. I've been running all this time, so I'm starting to get hungry. Where were we going for dinner?"

"About thirty li to the northwest, there's a small village hidden in a hollow called Chajapchon. We can stay there and watch the sunrise over Chajap Lake before heading back."

I am a Borax person who was obsessed with sunrise and sunset.

This morning, too, he woke up the group in the dark and watched the sunrise in the cold, and shed two more tears, or to be exact, two ice drops.

As I looked around Chajapho and headed northwest, the sun was already setting.

The cloudless sky was burning quietly.

It was a blue that was originally strong against the cold, but if you wear thick clothes over it, wouldn't it actually make you feel warmer?

Next to me, Yi-mei Gunyeong was linking arms and the feeling of the salt being crunched underfoot was surprisingly pleasant.

Inside the fur-covered face mask, Qing lips draw a pleased curve.

Since it'll be Lunar New Year soon when I get back, I guess I can have some fun and then go back leisurely.

Since Grandfather MuQing Mucheon told me to stop by Gongdongpa next time, I could stop by Gongdongsan on the way back to Gansu Province and then go home.

I'm starting to get hungry. What should I have for dinner tonight? It would be nice if I could get some bath water.

Qing hums a tune in a very good mood.

The original voice was a world-class beauty that penetrates the ears and steals attention, and the hometown melody that flows out without one's knowledge was a relic of a much later era that has a different level of excitement for the people of Zhongyuan.

So everyone smiled and hid their relaxed faces under their masks, feeling good.

Finally, at the entrance to Chajapchon Village, I climbed atop a slightly raised hill.

Somehow, countless birds would land in front of the village and form a flock.

It was a moment when the excitement that had been at its peak suddenly disappeared as if ice water had been poured over it or it had been hit with ice.

The Jang people of Qinghai practice bird burial.

Jojang refers to a funeral custom in which the body was left on the road for birds to eat.

This means ascending to heaven, not to the ground, and also giving the remaining body to birds to accumulate merit even after death.

This process was much more labor-intensive than you might think, as the carcass must be minced to make it suitable for birds to devour.

People in Zhongyuan point out that it was an uncivilized custom.

Smart people guess that digging down into the ground would have quickly resulted in frozen ground, making burial impossible, and that cremation was impossible in the village, where even fires were lit with the ashes of a tree, so that was the only option left.

This isn't the first time the group has been in a leadership position.

Having seen this kind of encouragement many times already, it's a little difficult to understand the emotion of remembering the deceased while looking at the devoured corpse.

Still, the atmosphere was the same, mourning the dead and comforting the bereaved.

But look at the flock of birds gathered here now.

It was as if all the birds of Qing sea had gathered and filled the village entrance with darkness. How many corpses were there lying around?

Fortunately, there were no flocks of birds on the road leading to the village, so it seemed that the body had been collected so that the birds would not be startled if someone heard it.

The group walked cautiously, making sure not to startle the people in the village, which was clearly in trouble.

But Chajapchon was quiet, like an abandoned village, with no sign of life.

There must have been someone who collected the body, but no matter how scared I was, I thought I would be able to hear their gasping breaths and trembling eyes because they were so scared, but all I could hear was a cold chill.

"Excuse me!? Is anyone here?"

It's the same even if you shout out.

The group looks at each other with stiff eyes.

"It looks like something big has happened. Just because it looks calm doesn't mean it's a good thing. It'll get dark soon, and there's no smoke rising from the fire. I think it'd be best to split up and search for survivors. Just in case there's that danger, let's split up and search."

Among the group, the best player, Qing, took the most pitiful Xue-i-ri, and the second best player, Jian Buxi, took the super-talented Pang-dae-san and the second-most pitiful Bong-sa-in to look around.

"It's so quiet here, so if anything happens, just shout. Keep your ears open, so fold up the hood of your fur hat."

Bengshi swallowed his admiration inwardly.

Heavenly Blossom Sword was always smiling and had a good smile on her face, but when a situation arose, she naturally had some kind of power to lead people.

Not only was his ability to be the youngest and highest level (since Bongsain didn't know about Qing's Hwagyeong and didn't flinch in front of Qingdo Bongsain), but he's also the president of the strangely named Half-Geom Ssangdohoe, a powerful social club where each and every member was important and everyone has their eyes on him.