\chapter{Chaka Salt Lake Murder Case (6)}

As soon as you open the door (or remove it), the sound of deep, wheezing breathing can be heard quite clearly.

The reason was that as soon as I opened the door, I was in the living room. I don't know if they call it that, but anyway, right there on the other side, there was a family lying on the carpet with a thick blanket over them.

Unless you're in a tent, you don't usually sleep facing the entrance of a building.

It's cold or hot due to the wind, the soundproofing was not good, and above all, people instinctively want to sleep in a safe place.

But why?

Because the bedroom would have been given to an honored guest.

After the group leaves, Qing hammers in a wedge nail and puts the door back on, then quietly closes it and goes inside.

It was a skill that was possible when a carpenter was also a master.

Qing raises his finger and brings it to his lips, then bends his wrist and points down at his feet, and finally points at the owner of the house who was soundly sleeping.

Quiet, here, they're watching.

Again, the fingers flick, and Yi-mei follows.

Of course, you don't know if the lama occupying the room was a master or not, so if he hasn't learned professional stealth, he might wake up at the sound.

But Qing was a reserve fighter.

Because the list of rare martial arts that the cheap guy told me about included a divine method for killing the Black Shadow's presence.

In this way, the two new models quietly slip into the living room.

A lama monk lying down, taking up all his space on the bed.

Qing was about to break the danjeon right away, but then he thought about it and realized that there was still no clear evidence that these guys were evil spirits.

Even if the evidence was certain, you won't know unless you check it first.

"Excuse me, monk?"

"omg!"

As soon as he was called, the lama opened his eyes wide and straightened his upper body.

Well, I was sleeping alone when I suddenly heard a voice calling from above my head.

It must have been a heart-sinking and terrifying experience for the martial artists unit, as it meant allowing someone to approach them while they were completely defenseless.

And it gets even more terrifying when I see the thug standing on the bed with the knife over his shoulder.

"[Who were you?]"

Qing glances at Hyunghyung and takes a moment to think about what to say.

If the situation was already under control, it's better to just stall for time like this to reduce the pressure.

But what should I ask?

Why don't you deny that you killed the Jangjok people and then be left speechless?

Then, as if you already knew.

Then, if you feel wronged, you will really feel wronged, or you will think that you already knew everything.

"[Father's Revenge. Chajapchon.]"

"[Chajapchon? I don't understand what you're talking about. What kind of strange things were you talking about?]"

"[That Buddhist man was so afraid of death that he even lies. I was watching with my own two eyes. What excuse do you have?]"

"[Ahem. There seems to be a misunderstanding. I'll forgive my rudeness, but put your sword away. It's Chajapchon. What trouble has happened there? I'll listen, so put your anger aside.]"

"Are you sure? You had nothing to do with the massacre at Chajapchon? Can you swear on your own asceticism and Buddha?"

"[Yes. I swear.]"

An oath without the slightest hesitation.

He puts his sword away.

As soon as that happens, Parak! A palm extends towards Qing.

The strategy was good, but, well.

How could those who robbed and stole, saying things like "Tibet" or "this and that", not be able to sell the Buddha and the monks?

The knife pointed at the neck was a trick.

The true threat that Qing had prepared was not the sword, but the feet, which were stretched out behind him, their center of gravity empty, and their hind legs ready to spring forward at any moment.

Before the lama's career could even begin, the sound of the wind was fierce and fierce.

It was so ominous that I couldn't believe it was the sound of someone swinging their feet.

The toes of Qing shoes were buried deep below the lama's navel, almost to the ball of his foot.

The feeling of the ominous energy of the Pacheon Magic shattering her dantian causes Qing's lips to slowly curl up.

Hiya, I feel so relieved.

This pair of bastards. What kind of Buddhist was this guy who asks questions and even sells Buddha?

"Ah."

Thanks to this, the head that had been stretching out claws helplessly at the air, and the mouth that was about to let out a scream was blocked by Jian Buxi's vicious hand.

The blood flowing down Jian Buxi's fingers was because her dantian was broken.

Whether it was because he was suffocating or because of the instinct of a person with his mouth shut, the lama's arm started to hit and scratch the forearm of Jian Buxi, causing a ruckus.

But even so, he was still a guy with a broken danjeon.

Even so, you have to struggle against less advanced players in the later stages.

Qing grabbed the lama's arm and squeezed it.

It might be sad if only one side breaks, so break the other side too.

Because there has to be a balance.

While the muffled scream lingers, unable to escape, Qing's foot gently lands on the lama's shin.

Qing's feet suddenly sink into the bed.

The soles of the lama's feet shoot up into the sky with the sensation of his shins snapping.

The lama's eyes roll upwards.

But that too for a moment.

He was so happy that he was jumping up and down with joy when Qing gave him a hand-made, or rather, a foot-made, reverse joint on his opposite shin.

The arms flap and the broken forearms flail, not knowing what to do, somehow reminding me of the air dolls of my hometown.

Oh, there was something like that too.

"Ugh!!"

But even so, it seems that the noise couldn't be hidden, as screams of pain and shouts of "Who were you?" could be heard from outside.

Then the door to the bedroom bursts open and a man rushes in.

Then, seeing the sight of a lama struggling with his limbs crushed, he collapses.

Qing Deeng rings the bell and speaks to him kindly.

"Don't worry. This bastard isn't a monk, he's a murderer who's run away after killing someone. He's a terrible demon who only kills good Buddhists who offer him a place to sleep. You almost got into serious trouble.

"[I, really!?]"

"[It won't be long before the truth about what these guys have done becomes known here. As far as we know, they were cannibals who massacred three villages and devoured their flesh.]"

"[You, you damned bastards! How dare you impersonate a monk! How dare you!]"

What was this? Does this work?

I said it as it came out, but Qing was surprised when he immediately agreed and changed sides.

Well, the words of the chief of Qing House were much more fluent than those of the residents.

And the miserable state of the lamas actually increased their credibility, because for the Jang tribe, monks were the ruling class, and impersonating them was the greatest and inviolable sin, like treason in Zhongyuan.

So, the horrific sight of the lama struggling with his limp limbs flailing around was more convincing.

Anyway, Qing doesn't know.

If it worked, that's fine.

"[There were more of these guys, and if they find out their identities were revealed, they might try to silence you. So, please leave your home and seek refuge for the time being.]"

"[That, that kind of thing.]"

"[Right now. Before those hordes of imposters and cannibals find out. And keep this quiet for at least three days. Who knows how many more of their gang there are?]"

Then, the man hurriedly urges his family to pack their bags and leave.

As I opened the door, I tilted my head for a moment, wondering if it was originally supposed to be hung like this, tilted towards the outside.

The way to stop screaming was very simple.

If you just make a hole in the gap between the collarbones, you can only hear the colorful breathing sounds and not scream.

At Qing's wink, Jian Buxi tightly blocks the windpipe at the base of his neck with his finger.

A scream of "Ugh," erupted, but there was no one there to feel sorry for it.

Isn't he the bastard who annihilated three villages and massacred civilians who knew nothing about martial arts?

"[Why did you do that?]"

"[Keuhe, those traitors who have forgotten their roots don't even deserve to breathe. They can't even pronounce our language properly anymore. Even the most insane ones were trying to celebrate the Chinese New Year, even though the New Year was still far away.]"

That was the reason I had roughly guessed.

According to the Western calendar, the new year begins in spring and ends in winter, unlike in Zhongyuan.

That is, there was still about a month and a half left according to Zhongyuan calendar.

Of course, Qing doesn't know that far.

I just remembered the broken lion head and the people who were dead there.

It was an absurd and outrageous statement.

The current Qinghai land was simply inherited from the previous dynasty roughly three hundred years ago, as the dynasty changed.

So, it has been a long time since the people of Qinghai lived as people of Zhongyuan for three hundred years.

Nevertheless, aren't the Zhuang people seen on the Kunlun journey still living while keeping their customs well?

Even the words of the preface were understandable, so isn't it a root that has been passed down from adults to children for three hundred years, and from children to their own children?

How about in the Qing hometown way?

Where did those Joseon people come from wearing hanbok and build Western clothes and Western buildings? They were slaughtering people by calling them traitors who don't even know their roots.

"Yi-mei, you're not a kid who can communicate anyway. Just tear your breathing hole even bigger so you can't even open your mouth."

"huh."

If I were to ask, how many Lamas there are, how many of them were experts, and whether the traitor was talking about Amukhaprap.

They say that it's scary when a fool has convictions, but aren't those who start wars, talking about past glories, just common idiots even in the Qing Dynasty's limited knowledge of history?

He roughly crushes the shoulder blade and then kicks the pelvis, shattering it.

It's funny how he's gasping for breath through his exposed throat, but he's also squirming in pain.

"[I don't care if you live or die, so just struggle on your own. If you're going to survive, it's better to live as a limbless crippled person. If I were you, I'd rather bite my tongue and die. Oh, right. I'm a guy who's so desperate to live that I'm willing to betray Buddha and the monks. I wonder if I'll have the courage to do that.]"

The lama monk, who had been glaring at him as if he was going to kill him, bared his teeth as if to show off, took out his tongue, bit it, and ate it.

Blood immediately started to flow out and the corners of his mouth were covered in blood, but he forced a smile and looked at Qing as if to ask how things were.

"[Are you an idiot? Dying by biting your tongue was actually blocking your airway, right? You think you can die by biting your tongue when there's already a hole in your throat? You really did what I told you to do. You ignorant brat.]"

The lama's expression becomes distorted.

Qing giggles and writes on the lama's forehead with his fingernail.

Fake monk.

When Qing saw my handwriting with satisfaction, he tied a rope around his waist, a necessity found in every home, and took the rope in his hand.

"……! ……!"

The lama opens his mouth, but he'll probably just curse or ask for his life anyway.

"Let's go. There were only fifteen left."

"You're going to take it now?"

"Then why don't you take them? I can tell them this was what happens if they misbehave. And there were fifteen enemies. If you throw in one wounded one, wouldn't that at least reduce one of them? If you take them as hostages before that, they can be used as shields."

At that, Paengdaesan's eyebrows twitched.

"No, I'm talking about your reputation."

"Hey, what about face? What face do I have in the first place? Do I still have any face left to maintain?"

"That's true, but still—"

"Fine. Even if there's such a thing as "saving face," I'm not ready for that yet. I'm officially twenty-one. Isn't that the right time to act recklessly?"

"Normally, you wouldn't use that as a shield. Hmm, shouldn't you at least pretend to stop them? You're going to drag around an enemy whose limbs have been broken."

"No. Cruelty was also a means."

"Huh? Why? Since there were so many enemies, wouldn't it be better to have at least one hostage?"

Both women grew up in brutal barbarism, so I wondered what the problem was.

Unfortunately, only one person in the group had any common sense. In a situation like this, wouldn't that woman, rather than trying to stop him, go even further and claim he was the one who'd be taking the blame?

Then he's a guy who'll just leave, no.

Brother Nan-gong, absolutely not.

Miss Gongsun, if you have something to say, you will hold it in.

As Paeng Dae-san recalls each member of the Half-Geom Ssangdohoe, he finally reaches enlightenment.

Half-sword double swordsmanship, was this really okay?