\chapter{Chaka Salt Lake Murder Case (1)}

Okrugeom Bongsain was a man with a gift for words as well as a rich sensibility and tearful ducts.

"Chajapho was also called Qingongjigyeong (a mirror reflecting the sky). It means "mirror of the sky," and so the vast salt lake perfectly captures the sky. For that moment, it's an absolute wonder, unparalleled by any other famous spot in Zhongyuan. Can you imagine the feeling of standing on the boundless sky, the vast expanse of sky stretching out above the earth?"

Behind me, the snow-capped mountains spread out, and soon the world reflected on the water was turned upside down.

The most spectacular sights were those of sunrise and sunset, when the sun was closer to the earth because it was in the open sky, and the sunrise and sunset were twice as splendid because there were two of them.

A dying dawn, a blood-red death between the split night sky.

And as the red setting sun set, the sky burned, and the crimson sky reflected in the salt lake spread out above and below the sky, filling the whole world with a burning red.

I described the spectacular scenery in detail to Qing, who was interested in the salt lake. The praise from Bongsain, who was surprisingly good at reciting poetry, was so great that I felt like running out and going to see it right away.

There, at Hwalongjeomjeong-

"When I saw that magnificent sunset, that dreary apocalypse that seemed like the end of the world, truly, the emotion was…."

Tears were falling from the eyes of the borax man!

What a moving sight that must have been!

Just thinking about it makes me shed tears without realizing it?

Besides, isn't the salt lake a spectacular sight that everyone has wanted to see at least once since ancient times?

Of course, that salt lake was not here, but another lake on the other side of the world.

I don't know about Qing, but objectively speaking (excluding the evaluation of the people of Zhongyuan), in Qing's hometown, even if it was called a salt lake, it was evaluated as being at a level of a deteriorated version.

Even if Qing knew this fact, it's not like she could go see it.

So, she was a transcendent beauty with a pale face, but her face looks natural, and she was a master of makeup, not just a master, but a virtuoso. Instead, she speaks to Jang Moon-in with the appearance of having not applied makeup to her neck due to carelessness.

"Sir, since I've come all the way to Qinghaiseong, I'm thinking of stopping by Chajabho. I heard it's such a spectacular view."

"Hmm? You mean the tea house? This winter?"

The expression on Cheonbija's face was strange.

He had an expression as if to ask what on earth he was talking about.

Qing asks him cautiously.

"Is there a problem?"

"What was the water level like this year? It's said that Chajabho Lake was dry in winter, so it's hard to see water. This time of year, it's usually just a salt flat with a few puddles. If we're lucky, there might be a few decent ponds left."

Kkwang!

This was the moment when Qing's expectations crumble.

No! My salt lake!

I don't know since when the salt lake was mine, but anyway, Ximen-Qing, frustration.

But frustration makes a man!

If you didn't know, you wouldn't know, but a man like Ximen Qing couldn't come all the way to such a remote countryside and just give up.

Why was it that even if you were lucky, there was still hope?

"But if there was still some water left……"

"You have to be lucky to see it. Well, for someone from the mainland, it's still a sight to behold. But if you really want to see it, it's better to go to Charihanho. No, that's too far to go in the winter."

"Is this Charihanho?"

"It's a beautiful lake, a dazzling emerald green. Even in winter, it's abundant water and never freezes, making it truly a breathtaking sight. But it's so far away. Let's see. It's roughly twelve hundred li from here."

"Hmm. It's really far."

"Not far."

Even so, twelve hundred li was not enough.

So, a round trip of 2,400 li, so one li was 400? Then… … , um. It's far.

"The Lunar New Year was in a few days, but the Lunar New Year was not over yet."

The Lunar New Year. This was one of the main reasons why Qing stayed in Kunlun to recuperate until he recovered.

Anyway, even if I go back to the shrine, it will take at least a month, or two at the longest, so I missed the New Year.

So I'd rather go and celebrate the Lunar New Year.

But it's said to be the biggest holiday in this neighborhood, so it's a bit awkward to celebrate it on the street.

I don't care, but my friends do.

Still, it would be much better to celebrate the New Year with the Kunlun School Taoists and offer blessings before leaving, rather than going to an unknown city.

"I'm planning on coming back before then. Two days to go, and two days to see everything and come back. Wouldn't five days be enough?"

"Yeah. It's the perfect schedule for a sore throat, but that's youth, I guess. It's really nice. It's cold, so be careful. Ask Sain-i to be your guide."

"Oh, I hope I'm not causing trouble."

"What's the nuisance? Doesn't that guy climb to the top of Ilwolbong Peak on a regular day and look out over Qinghai Lake? If you ask him to go see the scenery, he'll go with you even if you say no."

So this time it's the tearful swordsman, Bongsain.

"No, you borax-in-so-hyeop? How could you do this to me? You said there's no water in Chajapho in the winter? You made people so excited, and now you're doing this? I never said Qingongjigyeong was limited to the season."

In fact, the seasonal limitation was the same for salt lakes on the other side of the world, but Qing, who was born in the humanities, doesn't know about that.

"Oh. Oh dear. I guess I didn't tell you about it. It was so beautiful that I got so excited I couldn't help but ramble on. Then why don't you come and see it when it's in full bloom, around July? The salt lake doesn't go anywhere, so if you time it right, you can see it anytime."

He was a bum who showed no signs of reflection.

Well, that's close to home, so I can go out and see it whenever I want in the spring, summer, fall, and winter.

"Even if I rush to Seonyeong, it'll only be a month. When will I ever be able to come on a tour again at the right time……"

"Hmm? Then it only takes a month?"

This was the difference between people living in the center and people living in the countryside.

If you're going to join the Wulin Alliance, you should set aside about two months to do so, so one month was just enough time to leisurely enjoy the feng shui and have fun.

The same was true in Qing's hometown.

For a person in the capital, more than half an hour was too far for a person to reach.

But as the country people ask, wouldn't an hour's walk be a reasonable distance?

The concentration of leisure was different from the beginning.

"But Chajapho Lake in winter was also a spectacular sight. The salt-white ground was a sight you won't find anywhere else in Zhongyuan. Yes."

"Then, can you see the lake reflecting the sky?"

"I can't guarantee that. If we're lucky, there might be a large pool or two left, but, well, how much was that this year?"

Just as Jang Moon-jin did, Bong Sa-in also complains about quantity.

I don't understand Qing one a bit.

What, do you really need to think about how much rain or drought we've had this year?

However, for the people of Qinghai, the term "water quantity" includes not only rain but also water that falls from melting ice on mountaintops.

Thanks to this, the people of Qinghai always say things like, "How much was this?", but this was not a way of remembering, but rather an indirect way of saying that they don't know.

"Oh, you're going to see the tea master? Well, I'll show you around. But the Lunar New Year was in two days, so you can't go. If you try to go before then, wouldn't it be too tight?"

"I just wanted to go and take a look and come back quickly."

"Hmm. That's not the fun of traveling. A five hundred mile journey, stopping at villages along the way, making friends with the simple people of Jangjok, and taking your time going back and forth like that, it takes about a month…"

"Because we shared a lot of friendship along the way."

"Haha, that's true. Since you came from down here, aren't those southern Jang tribes so kind? I sometimes go down the Sacheon Road when I go to Zhongyuan, and that's why I always come here to show my face."

Even if you go to Zhongyuan, you're still heading to the Wulin Alliance, so if you go to Sacheon, it's like taking a long detour.

"A leisurely journey was nice, but sometimes it's nice to speed things up. I, too, have been longing to see the winter Chajabho. Now that it's come to this, would it be alright if we could hang out together?"

Well, I know he's a kind and generous person.

For some reason, the mountain was acting friendly for once.

Qing got a guide.

So, the Chajabho cruise begins.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The road that goes down the western slope of Mt. Ilwol.

Beyond the bare trees of winter, a vast lake like the sea unfolds.

Qinghai Lake.

It was the largest lake in Zhongyuan, and its area was equivalent to 0.5 Gyeonggi Province when converted to the unit system unique to the Korean people, the spiritual root of the Qing Dynasty.

However, it was only famous as the largest lake in Zhongyuan.

The preference of the people of Zhongyuan, as revealed through literature or poetry, was very low, and the reason was simple.

It's too far.

Since the area that the human eye can capture was limited, any large lake will appear large.

However, Dongjeongho and Taeho were wide and close, and the surrounding mountains and rivers were beautiful and splendid.

But since it was a salt lake, there were no trees, and the white roofs of the Qinghai Lake were beautiful against the backdrop of the distant Qinghai Mountains, but that was all.

However, when outsiders visit Qinghai Lake, there was a method of sightseeing that was highly recommended: riding a horse and riding along the waterfront.

The group descends Mt. Ilwol and arrives at Haenam-hyeon, located below, to buy horses.

It was a primitive ancient rental method where the horse's condition was checked and a small amount was deducted before being purchased.

It was also notorious for being a very difficult place to navigate without proper local guidance due to the various nightlife options.

However, the Bongsa people were disciples of Kunlun, and at least in the vicinity of Mount Ilwol, there were no big businessmen who would dare to troll Kunlun disciples.

So the group rode on horseback-

"I want to ride with Miss Ximen. Let's ride together. Please give me a ride. Okay?"

"No, you're calling yourself a wolf again? were you a wolf? were you saying that in your right mind?"

Of course not.

Because the tips of Xue-i-ri's ears, hidden by the fur hat, were very red.

But it was a theory that continues to worry the Qing because it was well-received.

The embarrassment was only temporary, but if you ride a horse, you can stay with her for half a day, and you can help Ximen Sojeo in case of emergency.

"Hey, come here? You know how to ride a horse, don't you? You know how to drive a carriage, too. You're not lying because you want to ride with me, were you?"

"If I ride a horse in the ice palace-"

"Ah. Okay. That's it."

There was no master who makes his servant ride on a horse.

Well, I guess so… … .

Qing stopped talking behind Xue-i's back for the sake of her reputation.

Still, it's better to be known as the Princess of the Ice Palace, since there's no need to bring up her past as an untouchable slave.

However, Qing didn't pay much attention to the fact that Xue-i-ri didn't respond in a strange way as usual.

Xue-i-ri did not answer when asked if she knew how to ride a horse.

But since he didn't say anything that was nonsensical, he would have been beaten up if he had ridden a horse, saying, "What kind of arrogant mongrel was riding a horse?" So, in any case, he didn't lie.

So, five people and four horses gallop along the riverside with Qinghaiho on their sides.

Qinghai Lake was a salt lake with accumulated salt water.

So, in winter, Qinghai Lake was half as salty as the salt water, and the water was frozen in a rough manner, and countless ice floes float around, as if it were the northern or southernmost sea of ​​the other world.

The view from atop a horse galloping with only its eyes exposed and wearing a thick fur coat was truly exhilarating.

But. A little. Ugh. My butt, ugh, ugh.

It was almost completely healed, and I still had a slight muscle pain that didn't hurt unless I pressed hard.

Horses were creatures that run up and down, and when you keep hitting your butt, you feel like you're building up a lot of muscle and then running again the next day without rest.

"Haha! That's good!"

It was a bonfire that made people shout out that it was good to see the sky soaring.

"Really, riding with my friends! How, how…"

Doesn't the back of the scream feel damp?

Qing glanced at him and saw that the man had long, scraggly eyelashes that looked like they had round ice droplets hanging from them.

Well, indeed, the Okru Sword.

The horses, excited to finally be carrying guests, gallop briskly.

These horses were sore from not being able to run because it was winter, and they had been running on this road their entire lives, so they had no reason to be afraid.

So, in reality, the words go their own way and the person was placed on top of them.

So, on the first day of the journey, I rode a horse, ate food and bought snacks at the stable relay stations along the way, and rode on through the ancient primitive rental system where I exchanged money for a new horse.

So we arrive at the last magic square, a small village called Munpa Village.

And then it was already just before sunset.

In fact, Qinghaiseong was a place where the sun sets very late even in Zhongyuan.

Even in December, when the days were short, the sun doesn't set until after 6 p.m.

So, that's it for today's journey.

Today's travel distance, 300 ri.

Less than 180 li to Chajapho.

Special note: severe pain in the buttocks of the patient.