\chapter{Journey to Nanning (4)}

Qing was contemplating whether the face was the one she knew, or if there were multiple Yangsanbo bases in Nokrim, and Dow Sam was not actually a name but a title used by the leaders of each base.

"Sura's Rampant Axe!" "Dow Sam!" "Sura's Rampant Axe!"

Ah, so Dow Sam was a famous person?

Since there was an escort among them who shouted out Dow Sam, it was clear that even if he didn't know who Dow Sam was, he might have at least called out his name out of courtesy.

I've done that a lot too. I know how that feels.

That aside, Sura's Rampant Axe, huh?

Qing now realized that Dow Sam, the hopeful father, had a pretty cool nickname.

So, Dow Sam, the leader of a gang of bandits, was quite famous, huh?

Of course, a Master of the Unrestrained Realm would be famous. Who wouldn't be?

This was a truly thoughtless presumption.

"Keuheuhu, everyone seems to know me well. Then there's no need to talk further, right? Hand over the toll."

The last Dow Sam was a bastard who was rotten to the core just by looking at his Karma, but at least he was a serious and weighty person.

It was unknown whether he had changed because he had returned from the underworld, or if he was just not meticulous enough to imitate even the personality while pretending, but…

"We will pay. How, how much do we need to pay?"

"Well. Let's see. How much should I receive to make it known that I received it well? Hey, Heavenly Slaughter, how much do they usually receive? I'm sure a Master of the Unrestrained Realm wouldn't receive a toll in a way that's too shabby, right?"

However, Qing had no intention of interfering and saying, ‘Hey, escort, that guy is fake. He's a fake Dow Sam!'.

She had learned, while paying with her body, that she should not carelessly rush into things when her body was not in good condition and the identity of the opponent was unknown.

Didn't I get hurt in the Zhangjiajie because of that?

If Ximen Surin found out, she would shed tears and perform ancestral rites for a month to thank the Divine Maiden and the Luminous Maiden for her disciple finally learning how to think.

It was a growth that would have made her eat ceremonial rice in gratitude.

Qing quietly and calmly assessed the size, number, and approximate level of the enemy.

As her eyesight was terrible, her hearing became more acute.

Countless breaths in the roads to the left and right.

Shit, there are ambushes on both sides, and the number is… What kind of bandits are these?

It was then.

"Ah, right. The toll is one head per person."

"Keke, Senior Brother, if it's one head per person, doesn't that mean it's counted by heads? Then, shouldn't it be the whole body per person?"

"Same difference. Now. If you hand it over obediently, I will spare your lives."

It was a line that Qing could have said.

In fact, Qing listened with admiration.

Hand over your head. If you do so obediently, I will spare your lives. Oh, not bad.

The bandits' intentions were clear.

They were saying they would kill them all.

At this, Head Escort Zhang was taken aback.

"H-How, how can you do this……?"

"Kyahaha! This body is Dow Sam of the Yangsanbo of Nokrim! If you want to resent, resent me! Now, all troops, no, brothers!"

The moment the self-proclaimed members of the Yangsanbo were about to rush forward, each wielding their weapons…

"Wait! Ugh."

Shit. It hurts my torso when I shout.

Just when Qing pinpointed the perfect timing to interrupt right before they charged, the bandits looked at her, wondering what was going on.

Qing limped forward and as she passed Head Escort Zhang, she whispered.

-There are ambushes on both sides. Many of them.

Head Escort Zhang's expression hardened.

This old man… He doesn't know how to manage his expressions…….

So Qing quickly opened her mouth.

"Wait a minute. I'm on my way from Zhangjiajie, and Dow Sam, the leader of the Yangsanbo, is dead. But here, there is someone claiming to be Dow Sam? Who are you?"

"W-What are you saying!? Dow Sam is dead?"

"His neck was cut off. And the Yangsanbo is also ruined."

Then, Qing thumped her staff on the ground.

The bandits looked at Qing's staff, which seemed a bit too heavy and had a uniquely vicious functionality that didn't give up on both the hammer and the mace.

They were shocked by the new cultural artifact, and they all looked at it as if they were fascinated.

Qing took stock of the situation.

These fuckers aren't from Nokrim.

The spiked mace had been polished, revealing a black dragon that was engraved (though Qing didn't know who did it since she was just a baby carpenter, not a baby blacksmith) coiling around the staff and ascending.

However, since the spiked head was pointed towards the ground, it looked like it was descending to the earth.

It was an eye-catching weapon at a glance.

If they were bandits from Nokrim, especially if they claimed to be the elite Yangsanbo, they wouldn't be able to not recognize their Chieftain's weapon.

Just in case, Qing checked again.

"Don't you feel anything after seeing this?"

"It's a unique weapon. Is it somewhere between a hammer and a spiked club? It looks heavy, though."

"It's not that heavy. About four geun?"

At this, the bandits looked at Qing as if they had lost their minds.

"Shit. You can't recognize this. Come over here and take a closer look. Do you really not know what this is?"

"What is it? Just say it. Just say it."

"Is that so? You don't know? ……You don't know, huh. If that's the case… Yeah, that's right. I guess you can't assess that fact just by looking at this yet. But, no. This story is, umm. Yeah, it's too early for you. But you'll know when the time comes. Let's stop this story."

A blood vessel bulged on the forehead of the fake Dow Sam.

"What are you talking about? Is this bitch crazy?"

"Have you never questioned the meaning of your existence, your reason for being? What kind of being is Dow Sam, really? Was that name given to you at birth, or did you choose to be Dow Sam through your own will? Heh. Judging by your expression, it seems you don't know. Then let me tell you, ……no, let's stop this story here. It's too early for you."

Dow Sam felt an inexplicable frustration, as if he had swallowed a sweet potato without even chewing it.

"Agh, what the hell is that?"

"Not knowing even after seeing this, you have also become so complacent. However, memories are not fixed. Now, would you look at this again? Here, can't you see the inscription written here? Now, look at this."

Qing pointed to a spot on her staff.

"A dragon pattern? What about the dragon pattern? Though it is indeed blasphemous."

"Hmm. Is that so?"

"What is it? Fuck! Stop talking to yourself and just say it out lo-"

"Shit, I'm frustrated too. Ugh. If you look at the inscription here, you'd know. Can't you see it?"

"I can't see anything but a fucking dragon."

"Shit! You can't see it because you're far away! Come closer and take a look."

Then, without realizing it, Dow Sam took about three steps forward before suddenly coming to his senses.

"You bitch! This is your plan to make me let my guard down! You want me to come closer so you can ambush me!"

Shit, it didn't work.

But Qing pretended to be unfazed.

"Then I'll throw it, so you can examine it. If you still don't ‘know' after seeing this, then it's really hopeless."

The ‘that' that Qing emphasized made Dow Sam feel incredibly frustrated.

What the hell is it? Just say it! Why are you the only one who knows?!

"Ugh, fine. Throw it then. Slowly. If you try anything, you know, right?"

"Of course I'm going to kill you. Catch it well. Don't scratch it."

Qing threw the spiked club upwards.

At the moment when the spiked club, drawing a parabola, fell and Dow Sam raised his arm-

Whoosh!!

Qing's palm strike flew towards Dow Sam's lower abdomen, or more precisely, even lower than his lower abdomen.

The Formless Palm Strike of Buddha's Palm was simply an incredibly powerful long-range palm attack.

Of course, a fist would hurt more than a palm, so there was some validity to the Shaolin monks' words that they forgot about Buddha's Palm after learning the Powerful Vajra Palm.

Of course, the best functions of the best internal cultivation methods were not included in the Powerful Vajra Palm.

If a guy at the level of a First-Rate Expert was hit by the merciful strike of Buddha infused with a lot of Inner Qi, their head would explode. But if someone at the level of a Transcendent Expert was hit, their skull would be hard enough to endure it.

So, what can I do? Hitting a guy in his most vulnerable spot is a bit embarrassing as a man myself, but we're not really in a position where we can afford such considerations, are we?

"Ugh!"

Dow Sam's lower abdomen received a powerful blow.

As a man's sorrow caused his back to bend sharply, the remaining hammerhead of the falling mace hit the back of his head!

"Argh!"

If a person was truly in pain, a scream wouldn't even come out.

So the scream that came from being hit on the back of the head with a mace meant that the pain of being hit in a man's most vital spot was far greater.

However, Qing had already soared into the air, exhaling the Heaven-Shattering Demonic Qi from her feet.

The five-geun ultra-heavy weapon, the Moonlight Greatsword, drew a half-moon with a yellow Sword Force.

Tuk. Dow Sam's head was severed once again.

In history, there were many who had died multiple times, but Dow Sam might be the first to have his head cut off twice.

At that, sparks flew in Qing's head.

Ah! My waist!

Pain is followed by hatred, and hatred is followed by strength!

You fucking fake bandit bastards!

It's all because of you that my waist hurts!

If the bandits had heard this, they would have shouted in protest that it was unfair to be blamed when they were attacked by real bandits.

But, if one wanted to be treated like a bandit, one must share the hardships that come with it.

It wouldn't be right to only pretend to be bandits when stealing, but not when being hunted down.

Qing's figure stretched out, and with the following trajectory, a bandit's head was split vertically.

At the same time, Qing shouted.

"What are you doing! Attack!"

Then the escorts rushed forward, each raising their weapons.

To be honest, escorts might have been one of the professions most exposed to real combat.

With the extremely cowardly tactic of three people teaming up against one, even though the bandits were individually superior, they were constantly pushed back, getting hit by swords and stabbed by spears.

On top of that, since Transcendent-Beyond-Transcendent-Qing was taking one down with each blow, they started to falter and then turned their backs.

Qing chased after them, but one of the bandits kept turning his back while bending at the waist, waving his arms as if telling her to get lost.

If he told me to get lost, I wouldn't have chased him in the first place.

Just as Qing took another strong step forward, using the explosive power of the Heavenly Demon True Qi…

Tung, Tung, Tung, Tung! The sound of something being struck hard rang out loudly.

Then, with a sharp swoosh, vicious screams of splitting wind. It was an ambush! And not just any ambush, but a fast one!

Without a moment's hesitation, Qing threw herself to the ground and slid.

Pababak, arrows rained down where Qing had been standing.

They were so powerful that they deeply embedded themselves into the frozen winter ground, leaving only the feathers sticking out.

Qing shuddered from the burning pain in her side and barely managed to raise her body.

"Keoheok……"

"S-Save me……"

Qing had rushed out to chase the enemy.

But the escorts weren't so proactive.

Because escorts were people who protected their clients.

They weren't hunters who chased down fleeing enemies until the end.

And arrows rained down on the escorts who were about to shout in victory after defeating the enemies.

They were very powerful arrows at that.

Even Qing couldn't dare to deflect or avoid them, and had to throw herself to the ground. 