\chapter{Journey to Nanning (2)}

Qing crawled on the ground, focusing on the sound.

"Cough……!"

Qing, in the posture of stretching out her arm to crawl, froze, and stood still like a avant-garde sculpture.

To be precise, she trembled.

What, what, now my body, how, what's wrong with it?

-Holy shit! Hey, did you just hear that? Did you hear it?

-What? Why are you suddenly acting crazy?

-Didn't you hear a moan or something? Shit.

-A moan? Maybe someone dying made it? I just finished off someone a moment ago.

-It was a woman's voice. A ghost, isn't it a ghost?

-You idiot. Why would there be a woman's ghost here? If there were, then I'd be down for it.

-What do you mean you'd be down, you lunatic.

The voices softly bickered, moving away in a friendly manner.

Yeah, I should get out of here for now.

Qing gritted her teeth and crawled again.

Stupidly, she had been lying on her injured side and stretching her arm out, so naturally, her body weight pressed on it, causing her pain.

She lay on the other side and crawled with one arm. Ow, they said the Grand Elixir was the best medicine and another life, but was that true? Why does it still hurt?

The Grand Elixir specialized in internal injuries and restoring energy. External injuries originally took time to heal.

Applying golden wound medicine could reduce that time, but it didn't mean that new flesh would instantly grow just because she ate some medicine.

I should examine the wound first.

But I need to get out of here first to examine it.

When Qing had crawled about half a length again, she suddenly thought, Why am I crawling?

I can just rip through and get out.

Qing stood the long Moonlight Sword upright like a pillar, then used the Clear Purple Sword to create a skylight.

Examining the wound was a priority over getting out.

So she gently untied her clothes, untied her clothes again, untied more clothes beneath that, and after untying the clothes within those, she finally revealed the skin beneath the five layers of clothing.

The dim light coming in through the torn tent made the colors of the world blur and tangle. It was like looking through a camera with a broken lens.

Hmm. My eyes are still fucked.

This should get better in a few days.

Let's see.

The red thing is my chest garment.

The white thing is my flesh.

And the black mass attached to my side is…

"Wow. Shit."

I shouldn't have looked.

There was a funny trait about humans. Before directly confirming their injuries, they felt less pain. It was as if the level of pain was determined by their own observation.

If they saw that they were bleeding from a cut, a severe pain would suddenly surge belatedly.

In other words, the pain was felt properly only after seeing how serious it was with their own eyes.

Although her vision was blurry and she couldn't see well, she could tell that her side was black and swollen like a mountain.

Qing was a certified medical practitioner acknowledged by a doctor.

She pressed and rubbed her wounds, shedding tears because she was hurting herself.

Fortunately, the pelvis is intact, just a crack.

The lowest rib is also cracked.

The muscles are all torn. My abs will definitely be asymmetrical. I'll have to work out only the left side to balance them out after it heals.

There's pus in the spleen and it's swollen.

There seems to be fluid in the pleura too.

When there are cracks in the bones? It heals over time.

The torn muscles need medicine.

The spleen will recover over time.

The fluid in the pleura will also gradually drain over time.

Fortunately, there was no need for any special treatment. Time would solve everything.

Considering she was properly hit by that massive hammer, well…

This much could be called a good defense.

You did well, my body. You really are the best.

This is why you can be called the body of the Supreme Qing.

So the final diagnosis.

Am I dying? No, I'm not dying.

Can I move? Yes.

Can I move vigorously? If I can.

It will be incredibly painful, though.

Still, seeing the wound made the pain more bearable, even if it hurt more. Because I'm not dying.

She was a bit worried about the internal organ damage, but she had eaten the Grand Elixir, so she should be fine.

Thus, Ximen Qing was revived.

The vertically stretched tent was silently split open as Qing crawled out on all fours and then stood up on two feet with a groan.

Those guys seemed to be looking for something earlier.

That can't do.

Isn't it the right of the victor to acquire spoils of war?

Therefore, the belongings of the evil ones Qing killed belonged to Qing. Qing could do whatever she wanted with them.

These bastards, they're bandits, but they can't even let go of their professional spirit, sneaking in to steal other people's things.

Qing's eyes turned vicious.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Bae Jong-gu ranked 95th in the unofficial rankings of the Green Forest, and his official ranking was outside the rankings.

Since the Green Forest did not consider anything below 50th place as a ranking, it was unofficial.

Being unofficial was thoroughly unofficial, and he was friends with Tae Yoon, who was ranked 107th.

The reason they were friends despite the difference in their unofficial rankings was that if those outside the rankings carelessly acted like seniors and juniors, they would get beaten the fuck up by some tiny ass shits for imitating them.

If they were unlucky and the Seniors were in a very bad mood, they might even get beaten to death.

Thinking about it now, it was a shitty work environment.

He had been thinking about quitting for a while, but the reason he hadn't was because he had no other way to make a living even if he quit.

But the Green Forest was now closed for business.

With his third-rate skills, he would just end up doing chores if he went to another gang, and he didn't have any particular skills to make a living.

Then, a memory flashed through his mind.

‘Chief, isn't this a treasure map?'

‘Do you not know what a treasure map is? So where does it lead to?'

‘There are one or two such places in Zhongyuan. If we had a proper map, we could easily figure it out. Do you want me to get one for you?'

‘Oh. You can figure it out? So where can we get such a proper map?'

‘The Military Archives of the Regional Inspector.'

‘You crazy bastard, do you want to be chased by thirty thousand soldiers just to steal a map? This guy is talking nonsense because he hasn't been beaten lately.'

‘It's not as accurate, but the small strategic map in the Military Archives of the Guard Assistant Commander would be fine too. But you'd have to steal them by region. Ow, bones, you hit my bones. It's just that hard to pinpoint a location with just a piece of a map. I'm not really saying such things, ow, oww!'

Behind the building of the Brain of the Thunderous Gang, Bae Jong-gu and Tae Yoon, who were sitting on the ground twisting wires, overheard the high-level conversation between the first and second (or third) ranks of the Green Forest.

Of course, even at the time, the Chief knew there were two guys twisting wires outside, but he didn't particularly care, as servants were like objects that existed everywhere.

It was the same principle as how a customer wouldn't stop talking just because a clerk was within earshot.

But clerks are people too.

They have ears to hear, eyes to see, and a mind to think.

Now that things had come to this, there might still be a treasure map somewhere.

After all, wasn't it a treasure map?

If he could find it, his life would be turned around.

Let's make a fortune and live lavishly in the city.

With that thought, he had returned to this ominous field of corpses.

But all around were corpses, corpses, corpses.

Even those corpses were rarely in a complete form, and it was hard to suppress the urge to scream every time he saw an arm or a leg.

He even thought he heard a woman's eerie wail.

If it wasn't for Tae Yoon's goading, he would never have set foot in such an ominous place.

But what could he do when he was already here?

He prayed that the treasure map would be there, and also that no ghosts would harm him, continuously asking for mercy from Confucius, Buddha, the Three Sovereigns and Five Emperors, Guan Yu, Zhuge Liang, and all other divine beings he knew.

While searching the Chief's tent, Bae Jong-gu's hand paused. He had found an unnatural shape tied to the frame under the bed, which was quite luxurious for a bandit.

Bae Jong-gu looked around.

Tae Yoon had split up to look for valuables in other tents.

So, if he found the treasure map and hid it, he could have it all to himself.

But then he encountered a problem.

It was too narrow to crawl under.

He would have to break or overturn the bed to check the contents of the pouch.

But if he made noise, Tae Yoon might come.

He was too weak to overturn it alone.

So, what could he do?

Bae Jong-gu finally called for his friend.

"Hey, Tae Yoon! Tae Yoon! Here! Come here quickly!"

Bae Jong-gu was being loud.

But there was no answer.

Even though there was no way he couldn't hear him shouting in the quiet surroundings.

Considering Tae Yoon's personality, he should have run over shouting, "Did you find it! Did you find it!" as soon as he heard his voice.

"Tae Yoon!? Are you there?"

But the ruined camp, filled with nothing but corpses, was silent.

"Tae Yoon? Don't joke around. Are you there?"

It was then.

An arm stretched out from the entrance of the tent, waving up and down as if to say he was okay.

Bae Jong-gu, who had been scared, was startled.

"Aaaagh! F-Fuck, wh-who is it!"

Then, a head peeked into the tent as if to check on him.

Bae Jong-gu was relieved to see his friend's uniquely grinning face.

"You bastard, is this a time to joke around? Come here and help me turn this over."

But then, Tae Yoon shook his head.

"What? Why?"

Again, just a shake of the head.

"What, you bastard. Speak. Speak."

Then, Tae Yoon tilted his head as if he didn't understand what he was saying.

Suddenly, goosebumps rose all over Bae Jong-gu's body.

What kind of posture was required for a human head to peek in from the side at shoulder height?

No matter how much he bent his body, how could a human head look in while lying completely sideways?

"Y-You, you! What! How are you……!"

At that, Tae Yoon's head dropped down and then rose up, his peeking face bobbing up and down.

"Aaaaaaaagh!!!"

Bae Jong-gu screamed and fell over, crawling backwards.

Thump, he bumped into the bed and, using the momentum of pushing the bed with his back, he scrambled up, using the ground as leverage.

Then, thump.

Tae Yoon's head fell between his legs and rolled, lightly touching his precious area, and stopped, facing upwards. He met Bae Jong-gu's eyes…

"Uwaaaaaaagh!!!"

Bae Jong-gu screamed at the top of his lungs.

At that sight, Qing chuckled twice before grimacing, Agh, and spraying the Moonlight Sword.

It was because blood and oil had splattered on the head she had just attached.

The movement was quite intense, so she grimaced again, Agh.

"Hey, if you're going to take other people's things, I mean, this guy. Not even a dog."

Bae Jong-gu's trousers rapidly darkened, and to make matters worse, a sound of trickling water could be heard.

Tae Yoon's head, soaked and stuck to the source, was still grinning from when it was cut off. He was probably shedding tears of blood in the afterlife.

And then, as always.

Hand over everything you have, you little shit.

I-I'll give you everything.

Spill everything you know too.

I-I'll spill.

(Some bullshit about a treasure map)

And then, I can't forgive you for trying to steal my things!

Please spare me!

No! I didn't say I'd spare you!

But please spare me!

Then, crawl under the bed and bring out the pouch. I'm a bit uncomfortable.

(Some bullshit about Bae Jong-gu doing it)

Then, well, as always.

Good job! Now die!

You said you'd spare me!

You fell for it again! I didn't say I'd spare you!

"This is for trying to steal!"

A flash of the sword, and Bae Jong-gu's arm fell off.

"This is for what you did to Tae Yoon!"

The other arm also fell off.

"This is the wrath of the earth you've contaminated!"

And then his head fell off.

"Ah, I forgot to take my share."

Only then did Qing's expression contort.

"Agh…… Sssssp."

It was bearable when she was killing villains and playing around.

But now that she was done, her side was screaming. Why. Why did you do this to me? Do you not want to heal? Huh? Are you, by any chance, thinking of festering? Are you going to rot and become gangrenous?

What could she do about it?

She couldn't very well yell at her side to be quiet.

All Qing could do was endure, no matter how much it hurt and how unfair it was.

Qing opened the pouch and poured its contents onto the bed.

First, there was a Secret Manual.

It had a title written on it, but her eyes were messed up, so it was all blurry and she couldn't read it.

However, Qing's method didn't rely on her eyes but on her hands.

When she picked it up, the Martial Arts Window sparkled. It was temporarily registered with a red border. The letters were too small to read, so all she could make out was that the black part was text and the blue part was the status window.

There was a wooden box.

She didn't know what it was, but when she touched it, she could tell it was a medicine box.

When she opened it and smelled it, it had a nice fragrance.

But she had no idea what it was, since it belonged to a bastard who said eating people was no big deal.

Hmm. I'll have to ask someone who knows about this later.

And then there was something pink and flimsy, looking like a handkerchief. No, it felt like a handkerchief.

Qing recalled the appearance of the gang's leader.

A hairy man with an excessive amount of hair on both the top and bottom of his head, unfittingly carrying a pink handkerchief?

Come to think of it, the hair was excessive because it was genetic.

His daughter was also really amazing, like a rainforest, like coral reefs.

Ah? Was he going to give it to his daughter?

At that moment.

The Mission Window sparkled and emitted light.

Since a certain point in time, Qing had just immediately opened and then closed the Mission Window whenever it alerted her of a new update.

After all, no matter what the Mission Window said, Qing would just do as she always had done.

Killing bad guys and helping good guys if there were any.

But this time, Qing opened the Mission Window and stared at it.

\begin{quotation}
[Premonition, (Unknown)th Crisis]

[You have obtained the Treasure Map of the Shin Family Vault.]

Action for Mission Completion (Unknown)

[This choice may affect all under Heaven.]
\end{quotation}

But isn't it a bit too short? Is the content lacking?

Qing pretended to look at the status window.

She couldn't read it even if she looked, though.

Heh, you're frustrated, right? It's no use, since I can't see anyway.