\chapter{Journey to Nanning (1)}

The difference between Unrestrained Realm and Demonic Possession.

Rather than creating a martial art with one's own interpretation, it is much easier and faster to perfectly master an already completed martial art according to the intent of its founder.

However, just as it is easier to achieve Demonic Possession compared to the Unrestrained Realm, there is a side effect of being swayed by the martial art.

If the problem is going on a rampage while being swayed by a martial art, one might ask, "Why not enter Demonic Possession with a pure Divine Art of Daoism or Buddhism?"

However, martial arts are fundamentally a skill of murder.

They are techniques designed to kill others better, easier, and in greater numbers.

Therefore, if a martial art sways a person, even if it is a peerless Divine Art and not an evil Demonic Art, it will inevitably be captivated by the inherent purpose of martial arts, murder itself.

That is why martial artists in a state of Demonic Possession are called Demonic Humans.

And here, a Demonic Human was dying.

Only after vomiting about four bowls of blood did he finally come to his senses.

Wang Cheolgun now knew the state of his body.

Poison, it was poison.

The poison had already spread throughout his organs, so even without cutting open his stomach and taking a look, he knew they must be black, rotten, and decayed.

When was he poisoned?

Yes, that dagger.

Applying poison to daggers was the most basic tactic and common sense for those of the Unorthodox Faction.

"Kuhaha, to think I'd fall for such an obvious trick. My senses must have died too. Well, since my senses are dead, I should just die too."

Qing quietly observed Wang Cheolgun.

I think he's saying something.

Qing's condition wasn't great either.

First of all, she couldn't see properly.

The eye of the bandit leader, which had burned so fiercely, no longer burned. As such, there were no longer any light sources that caused her vision to spread out in a cross shape.

It was just a dark night, and something whitish was stuck to the ground, as if crouching.

That was all she could make out.

And her hearing wasn't any better.

She kept feeling like she was submerged underwater, muffled, with a continuous, annoying, high-pitched whistling ringing in her ears.

Still, if she stood still and concentrated, she could at least hear something.

"Let me ask you one thing. What did the Green Forest ever do to you for you to be so cruel?"

"Nothing! They didn't do anything!?"

Qing's voice was loud and clear.

Wang Cheolgun's expression twisted.

"You, are your ears? Hah, so I ended up like this because of a blind and deaf person? Hahahaha, keok, keheuk."

Wang Cheolgun burst into laughter, only to end up vomiting blood pathetically.

His heart wasn't really laughing, and now his body wasn't really laughing either.

"I'm not, okay? My ears are fine? And my eyes are fine too."

When she said so while her eyes were unfocused and her voice was far too loud and uncontrolled, it was no different from admitting that she couldn't see or hear.

At this, Wang Cheolgun picked up a stone from the ground and threw it with great effort, making a parabola towards the far left.

Clatter, the sound of a stone falling.

Qing was startled and quickly drew her sword, pointing it into the empty air.

"Okay. I believe you. You can see and hear very well."

"I don't know what trick you're trying to play, but it won't work on me."

"Yes. It really doesn't work."

Wang Cheolgun didn't even know that he was being sarcastic, but Qing just kept her guard up.

Regardless, Wang Cheolgun, with his life coming to an end, decided to satisfy his curiosity.

"You said you had no grudge, yet you acted this way? Then why did you kill my son so cruelly? He didn't even raid a bandit's den."

"Who said anything about raiding? I got off the carriage because I was passing by, and that's where he was. And when we haven't even exchanged names, how can someone just undress and spread their legs? Of course, I had to cut off his limbs."

"He's my child. The son of the Green Forest's Supreme Commander. Were you not afraid of the consequences?"

"That's the problem. Was he even Second-Rate? If a guy with no skills is going to go around swinging his dick just because he believes in his father, he should never have left the house in the first place."

Normally, he would have been furious.

But with death at his doorstep, his hands and feet felt as heavy as stones, and he had to exert all his might just to throw a single pebble.

Helpless, he could only let out a hollow laugh.

"Then, even if it was just for your son, was it necessary to be so cruel as to come to the main camp and kill my daughter as well?"

"Who said anything about coming to your camp? I was just passing by and heard that Zhangjiajie was nice. What was it again? ‘If you haven't been to Zhangjiajie, you can't say you're old even if you're 100 years old'? I just came to see what the fuss was about. It's good that you're proud and all, but what do I care where the main camp of the Green Forest is? I've never even heard of it."

This time, even Wang Cheolgun found it hard to just brush off.

His blood pressure spiked, causing blood to spurt out of his mouth along with pieces of his melted internal organs.

"Then, you weren't raiding us, but just passing by, and yet my son, why!?"

"Seriously, how did you raise your child? Did you teach him that he should undress and fuck any pretty woman he sees?"

"Hmph. A real man should act as such."

"A father like that is why his son turned out like that. But he really just tripped and fell while running away by himself. I didn't even touch him."

"My second was burned alive by you."

"Huh? Me?"

Qing asked back in bewilderment.

When did I do that?

"Did you not set fire to the main camp? Well, it's better than living like that and dying at the hands of an enemy. Yes, they both did something deserving of death. Then what about my daughter?"

"She was eating people alive. How long did you think she'd live? Seriously, if you're a father, you should have broken her legs to stop her if she was doing that kind of shit. How could you just watch as she did something so utterly vile?"

"Weren't they just ingredients that came in? Whether you kill and eat those who are going to die anyway or eat them alive, what difference does it make?"

"Wow. Your way of thinking is truly on another level. Then there's no need to answer the next question. Why did you fight the Green Forest? If you can't even overlook such utterly evil beings, are you even fit to be part of the Orthodox Faction?"

"Yeah. Bandits do bandit things."

It was just a story circulating in the marketplace.

A hero slays evil and saves people.

She was still young, so she had the bloodthirst and sense of justice to jump into a fire, a characteristic of an immature Orthodox Faction member who didn't know the ways of the world.

"Well. Kill me. If possible, in one blow."

Wang Cheolgun spoke thus and lowered his head.

However, Wang Cheolgun was a bandit to the bone.

Contrary to his attitude of submissively offering his neck, his hand, which was hanging down, was tightly gripping the spiked club, almost to the point of breaking it.

He was preparing his final move.

His life was going to end anyway. As such, the moment she approached to deliver the finishing blow would be the last moment of that bitch's life as well.

Did he open his mouth earlier because he suddenly felt like emptying his lingering attachments before death?

No. He was pretending to accept death, so the young girl would let her guard down and approach him.

Qing was tired.

She would have loved to flay him alive, but her body was a mess. Her eyes and ears were damaged, her pelvis and flank felt like they were broken and ached terribly.

And she must have rolled on the ground at least dozens, no, more than a hundred times.

Thus, there wasn't a single part of her body that didn't hurt.

So what else could be done?

Thus, Qing took a step. And then another step.

Wang Cheolgun, looking at the ground with his head down, wore a smile full of murderous intent.

Even if Qing could see his face, which she couldn't due to her vision, she wouldn't be able to tell, but Wang Cheolgun was suppressing his killing intent with all his might, thinking, ‘Come closer, just a bit closer'.

Then, suddenly, he heard a small exclamation.

"Yipe."

Yipe?

Startled, Wang Cheolgun raised his head.

He saw Qing pointing her index finger at him.

And her finger turned black.

A single ray of light, darker than the dark night, darker than darkness itself, shot out of her finger!

Wang Cheolgun twisted his body.

However, due to the terrifying force that pushed his shoulder, he ended up rolling on the ground for about half a zhang.

Since his insides were already ruined by poison, murky blood gushed out of him, mixed with pieces of black internal organs.

"You dirty, despicable bitch! Come closer! Come closer and behead me! You dirty whore! You fucking bitch, you cunt, die! I'll kill you!"

Qing clicked her tongue.

"Wow. Look at this. You're still using your Defensive Qi. I knew it. Why, you were going to try to smash my head when I got close, weren't you? Planning to die together?"

If one pointed, it made a popping sound and blew the head off; it was the Heavenly Demon's fingering technique, Heavenly Demon's Finger.

It was a technique Qing usually didn't use.

Because its efficiency was poor.

One shot of the Heavenly Demon's beam of death consumed as much as forty steps of the Heavenly Demon's March of Reign.

In other words, one shot of Heavenly Demon's Finger was equivalent to forty steps of Heavenly Demon's March of Reign.

The Heaven-Shattering Demonic Qi had a small capacity, so she couldn't waste it on a few finger flicks and lose her best means of rushing.

The beam of death was certainly lethal once it pierced the body, inflicting fatal wounds, but if it couldn't penetrate, it was just a strong push.

"Keoheok. Keheok."

"You old fucker, you're so full of tricks."

Qing extended her hand repeatedly.

With every ‘bang, bang' sound of a Buddhist temple's bell, Wang Cheolgun's legs bounced greatly as he was roughly struck by the force.

Since she couldn't see well, her aim was off, but she figured the lumpy part on top was the head, so the long parts below were probably the legs.

Eventually, after mangling both of Wang Cheolgun's legs, Qing casually asked.

"Mister? Are you dead? If you're not dead, answer me."

Wang Cheolgun pretended to be dead.

Now, all that was left was his will to not die alone and to drag that bitch down with him.

"Did he die? Did he die? Did he die? Did he die? Did he die? Did he die? Did he die?"

Qing chanted the spell of revival repeatedly.

Wang Cheolgun, who was listening, felt a sense of dread and fear.

She spoke rapidly, saying ‘Did he die' repeatedly, and since his ears were half-gone, he couldn't adjust the volume, so her voice was loud, making it seem like a madwoman had gone insane or was possessed by a ghost.

"I think he's a Master, so if I don't confirm his death, he might come back to life later and seek revenge. But he also seems like he's pretending to be dead to land a hit on me."

Pretending to be dead, Wang Cheolgun didn't know, but Qing was grinning as she spoke aloud for him to hear.

Then, she threw the torch in her hand, which landed on Wang Cheolgun's stomach with a plop.

Even if one's will was strong, they couldn't ignore the pain of burning flesh and pretend to be dead.

It was the sad limitation of humans.

"KAAAAAAH! KEOHEOK, KEOHEOK. AAAAK! XIMEN QING! I'LL KILL YOU! YOU FUCKING BITCH! I'LL KILL, KEOHEOK, KEEEEHEK, UWEK, KILL, I'LL KILL YOOOOUU!!"

"Wow. So vicious."

Qing clicked her tongue and limped, picking up the torches that had fallen on the ground and throwing them one by one.

The flames were fed with pine resin, so they burned tenaciously. As such, after a dozen or so torches were thrown, his clothes finally caught fire, turning him into a human torch. Wow! This! I know this!

The Honored One of Ash! I will become the kindling!

Qing threw more torches in excitement.

Even someone of the Unrestrained Realm could not withstand being burned alive.

Especially if one's legs were mangled by Force Palm Strikes and their internal organs were already ruined.

Thus, starting with agonizing screams of ‘AAAHHH, AAAHHH', the curses eventually stopped, leaving only pure, genuine screams of pain and agony.

In the end, Wang Cheolgun's desperate resistance, as he could do nothing but scream, ended when he could no longer withstand the flames burning his body.

Then, all that was left for Qing was a tattered body, pain, and wet clothes that felt frozen in the night wind. Ugh, it's so cold…….

Qing looked around.

I'm not in great shape right now, so I need a place to hide immediately. There must be bandits who fled nearby. I need to manage my internal injuries safely.

Then, something whitish and lumpy caught her eye on the ground.

Ah. It was said that the darkest place is under the lamp.

Qing crawled under the collapsed tent.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

There was a commotion, a sign of people's presence.

She tried to get up from her seat, only to let out a groan, ‘Ugh'.

It felt like thousands of needles were pricking her flank, causing a dizzying pain.

The expression ‘my vision turned white' was surprisingly accurate.

After all, one couldn't see anything when in such pain.

As soon as Qing came to her senses, she had to struggle to catch her blocked breath.

The pain subsided a bit before the heaviness that pressed down on her entire body was felt.

Only then did Qing fully regain her consciousness.

Ah. I took the Grand Elixir Pill and was circulating my energy when I must have fallen asleep because I was too tired.

Since it was pitch black under the thick tent, she couldn't tell if her vision had returned, but at least her hearing seemed to have recovered during the night.

There was a bustling crowd beyond the tent.

-Where was the Supreme Commander's tent?

-Isn't it over there? But what if he's not there?

-Then he's not there. What else? Both the main camp and the Supreme Commander are burnt, so if he's not in his tent, he's burnt and gone.

Hmm. It seems like those bandit fuckers are back, huh?

They must have returned to see if there was anything good left.

Hiding under the tent seemed to have been a good choice. If she had just lain on the ground or entered an intact tent to use a cot, she would have been discovered already.

But let's see.

What should I do now?