\chapter{Journey to Nanning (9)}

The original ancestor of the Red Great Justice and Wang Mang, the eldest brother of the Mangtakjo Eui!

While the rulers of Zhongyuan said they abhorred Wang Mang, they actually respected and worshiped him the most.

Wang Mang emphasized the integrity of public officials.

Therefore, he argued that government officials working for the country should not receive gold and silver in return for their work, and that they should serve the people with a pure heart, abolishing the salaries of all public officials.

This is why the rulers and officials respected and worshiped Wang Mang.

Since then, whenever officials asked for more gold and silver, more salaries, the rulers denounced them as corrupt, dirty, and greedy officials, drastically cutting their salaries.

However, they did not allow them to hold other jobs, so officials had to embezzle state funds to make a living.

In a way, it could be said that it was corruption to make a living.

A structure was born that was absurd for both the officials and the rulers.

A portion of the amount embezzled by the subordinates was passed on to their superiors.

Therefore, those who delivered more, that is, those who embezzled more, were promoted repeatedly, saying they were more competent.

How much one could embezzle, how ruthlessly one could exploit the people and suck their blood and tears, became the measure of competence.

And this ‘competence' of the people of Zhongyuan was a spirit of China that continued into the future, even in Qing's hometown, and could be said to be China itself.

And soldiers were also public officials.

In the past, present, and future of Zhongyuan, the Chinese army was famous for its lack of three things.

No military discipline, no military discipline.

No logistics, no logistics.

No mercy. Due to the collaboration of the first and second, pillaging was a livelihood, and they were earnest only in pillaging, showing no mercy.

Moreover, this pillaging did not distinguish between friend and foe, nor did it distinguish between barbarians and the people.

They don't catch criminals, they don't stop barbarians, they lose every expedition they go on, and when foreign invasions come, they can't stop them, and dynasties change, but they are an army that is only earnest in plundering their own people.

Why do they exist?

Well, to protect the stern dynasty of the Emperor, a sword that protects only the rulers of Zhongyuan.

So who would dare to criticize them!

If they don't do this, they'll starve to death!

What about their wives and concubines they have to feed?

Surely even the heavens would understand.

Of course, because they don't understand, Qing sees the red stains floating above the soldiers' heads.

Her eyesight was damaged, so she couldn't tell the exact numbers. But by looking at the length, she could tell whether it was three digits or two digits.

Qing, not knowing the situation, was just curious.

I mean, are the armies of the primitive ancient Zhongyuan gathered only from criminals?

When enlisting, do they check how evil and bad someone is and only let the real sons of bitches pass?

The answer was that if you enter the military, you naturally become a son of a bitch, but Qing didn't know that.

She didn't particularly want to know, and even if she did, she wouldn't understand.

If you've done something to die for, then you should just die, right?

Thus, Qing followed the bright red numbers with light steps.

The trees of the Nanling Mountains were refreshingly straight.

It meant that unlike the dense primeval forests of Zhangjiajie, which were packed both above and below, the trees here allowed for an unobstructed view.

So, if these two turned their heads now, they could easily spot Qing's figure, but…

At first, Qing was cautious.

But then she kept having doubts.

What's this? Walking so proudly? Just looking straight ahead?

A man never looks back?

So, since Qing didn't make any noise and kept her presence hidden, they just kept going their own way even though she was following them openly.

"But what does it mean to say that someone looks like a traitor at first glance? Does it say ‘traitor' on their face or something?"

"I don't know. They said he's a clumsy scholar, so I guess you can tell at a glance."

In fact, if the soldiers had seen Jayu's earlier appearance, they would have understood immediately.

If they saw a scholar wearing a purple robe with a dragon embroidered on it, even the descendants of the Tang Dynasty's army would shout, "Fuck, it's a traitor!"

"Ah, I want to pillage!"

"Don't talk so loudly, you idiot."

"Why? I heard that the Mountain Cleaving Army found a village the day before yesterday and looted it. They asked if they could share some women, but they said they wanted one silver coin. Damn it, they're not even pimps."

"One silver coin? Isn't that too much? Should we talk to Platoon Leader Cheonho?"

"Kang Cheonho doesn't have a head for that kind of thing. If we bring it up, won't it just cause more trouble? Or should we just attack and take them?"

"Don't be ridiculous. If we get caught by those guys in silk clothes, we'll all get our heads chopped off."

Qing, who had been listening quietly, thought. Death penalty.

But the Mountain Cleaving Army? Death penalty from the start.

Qing silently approached and tapped the shoulder of the one behind.

It was the kind of hand gesture where one pokes the cheek with an extended index finger, often used as a joke.

However, the difference was that the fingertip was glowing with a fingertip-sized blade of Sword Force, rotating and craving flesh.

It was a very minor difference.

And minor differences make masterpieces.

"Excuse me?"

"Argh, whaaaat."

Qing's finger pierced the soldier's cheek and penetrated the tongue inside.

The sensation of the inner joint grinding the teeth, and the harmony, or contrast, of the first and second joints cutting the tongue root?

Ha……. This is amazing…….

"Ehh, what's wrong?"

As the one in front turned around, Qing's Sword Tip plunged into the center between the man's collarbones.

The insides were blown wide open, and the windpipe inhaled fresh air through a new passage, exhaling stale breath, and the scream that couldn't reach the vocal cords leaked out as a sharp whistling sound.

"Aaaagh……"

Qing's finger then moved straight down, passing through the cheek and lower jaw to reach the neck, puncturing a hole in the windpipe as well.

Qing staggered back slightly.

Wow! The Wheel of Karma!

This is great, and Yeon Pa had been using this all to herself.

Qing's three Soul Flames flickered in her eyes.

Regardless of East or West, since ancient times, three has been a perfect number, and in Zhongyuan, it symbolized the Three Talents of Heaven, Earth, and Man, which could also represent the world, or space-time.

A gaze that truly contained space-time!

"Now. Kill each other from now on. Only one will survive. As my respected one said, he who seeks to die shall live, and he who seeks to live shall die."

However, the two were struggling to even let out a proper scream.

Qing stomped her foot to draw their attention and then said, showing her Sword Force.

"Can't you hear me? I don't need two."

At that, the two's responses diverged into life and death.

The one with the new path in his jaw immediately fumbled for his identification tag at his neck, while the one with the intact jaw raised his axe instead of his identification tag.

Crack. Thus, the one with the horizontally split jaw had his head split vertically as well.

The reason why loyal soldiers who knew the priorities of their duties were gradually disappearing from the army of Zhongyuan, and only treacherous potential traitors were increasing, was because of this.

Because the truly loyal ones could not survive.

"……!"

The one with the hole in his neck just gaped, unable to speak, and held out both hands.

He was begging for his life.

Probably his expression was one of supplication?

"Promises are promises. But before that, I'm curious about where the camp of those Mountain Cleaving Army guys is. Could you guide me?"

"……!"

At that, the man gaped again, then realized he couldn't make a sound, and nodded vigorously.

"Good to see you're cooperative. If you had resisted or tried to blow a whistle, I would have had to find someone else."

So, Qing followed the soldier's lead, not tiring even after traversing the mountain paths for over half an hour.

He must have really wanted to live.

Then, a hidden camp appeared beyond the ridge.

"……!"

The soldier tapped his chest and pointed far away with his finger.

May I go now?

At this, Qing shook her head.

"Eh. I told you. Those who seek to die shall live, and those who seek to live shall die. But you killed the one who was trying to die, so that has nothing to do with my promise. I did say I'd kill those who seek to live, right? Hmm. But since you were a guide, I'll only kill you halfway."

Well, there are a lot of people to kill anyway, so might as well be generous.

Qing's blade sliced through the soldier's belly.

Its contents spilled out, but maybe he'll live if he's lucky, maybe not.

Qing left the soldier behind and headed for the camp.

Even if it was a temporary camp, it didn't even have a stockade, just some ropes with bells tied to stakes in the ground.

It was a crude boundary that wouldn't hinder any martial artist, let alone Qing.

Qing infiltrated the camp like so.

----

When Qing returned to the crevice between the rocks, Jayu greeted her.

Qing thought that he must have been bored all day, not having anything to do.

"Are you back? So, did you find a way to escape?"

"Change of tone. I just rested for a few days and decided to descend the mountain? Those guys were a bunch of pushovers. I took out four of their camps, and it seems like in three or four days, there will be so many holes in their ranks due to lack of manpower."

"Hmm, your expression seems a bit dark for someone who says that. Is everything alright?"

"Yeah, no, it's just that the soldiers were all such scumbags? They pillaged every village in the vicinity. Not even bandits, no, they were worse than bandits."

Bandits at least did not annihilate entire villages, even if they looted them.

After all, they had to keep looting them over and over.

However, the soldiers were different.

There would be no future plundering, and fearing potential trouble, they eradicated the villages when they looted them.

It was evidence destruction.

Qing had only cleared four camps after a full day of searching. It took a long time because she was taking care of each one with great care.

At this, Jayu's expression also darkened.

"Ahem. It's an old evil, so there's nothing that can be done. If the soldiers were paid ample salaries, it could be prevented….."

Since there were as many soldiers in Zhongyuan as grains of sand, even a slight increase in salary would drain the national treasury.

Conversely, it meant that there was no need to raise the pay for such insignificant things like sand.

"Seriously, when I look at this, I don't understand how the world of Zhongyuan even functions."

To be precise, that was why it didn't function.

Discontent accumulated here and there, leading to warlords and powerful families raising flags of rebellion, causing the country to fall into chaos and resulting in the change of dynasties.

"Tsk tsk. It's because the current Son of Heaven lacks virtue. If a virtuous one sat on the throne, the world wouldn't be like this. Don't you think so too?"

"Ahem."

"What, are you sick? Why are you coughing? Hmm, maybe it was a bit cold for Jayu?"

At that, Qing placed her hand on Jayu's forehead.

The other hand snaked around her neck to check her pulse.

Jayu flinched and stepped back.

But Qing just moved closer by the same amount, and the grip of a Transcendent Realm Master was not something an ordinary person could easily shake off.

"Y-You, what is this, such an indecorous, why are you doing this?"

"Your pulse is a bit weak. But we can't light a fire. For now, try to endure by wearing another layer."

Jayu's face was already flushed red as she spoke.

"……I can't even put my arm in now."

Jayu had already put on four layers.

He couldn't even bring his arms to his sides and, in the first place, an outer garment was not an article of clothing with a generous fit like summer clothes.

At that, Yeon Pa scolded her.

"What's this about a weak pulse? What are you saying to a perfectly healthy person? Also, since when did you learn medicine? If there's no fire, then people should share body warmth by embracing each other. That's the best way."

"Ugh."

Qing was disgusted.

"Yeon Pa. Please don't."

Jayu was also startled.

But Yeon Pa was persistent.

"This old and lowly one would love to do that, but I'm afraid I might taint your noble body since I'm wounded. Since relationships between men and women should be distinct, you should do your best to preserve that precious jade body, shouldn't you?"

"Just lighting a fire would, ugh."

Then Qing suddenly realized something.

"Yeon Pa is an Unrestrained Realm Master. You can boil a water pouch, can't you? Just a cup of hot tea would warm the body quickly."

If one reached the Unrestrained Realm, they could even burn things or boil water with Inner Qi, using the so-called Three Fundamental Flames.

It was a principle of condensing Sword Force, so if Qing used it, it would only result in using a lot of Inner Qi to make things lukewarm at best.

But an Unrestrained Realm Master could at least burn paper.

So, boiling water should be possible.

"Oh, even if we're bundled up, the body should be colder after being still all day? Didn't you boil some water for yourself when I wasn't here?"

If it was Yeon Pa's personality, who cared deeply for Jayu, there was no way she wouldn't have boiled water for her.

Qing's eyes narrowed, and Yeon Pa grimaced.

"Tsk. You sharp-eyed wench, you're not very useful. Fine."

"Hey, wait, why should I be useful in the first place? And why are you suddenly cursing me?"

"Well. It's to conserve a bit of Inner Qi, just in case. Even a Master of the Unrestrained Realm wouldn't just use Three Fundamental Flames to light a fire. My Inner Qi isn't in the best condition either."

"Hmm."

Qing maintained her narrowed eyes.

That seems like a bit of a lame excuse… 