\chapter{Journey to Nanning (5)}

Qing gritted her teeth.

She wanted to chase after those bastards and kill them right away, but she couldn't leave the injured porters and workers, who were writhing in agonizing groans, behind.

After all, Qing was the only one who could at least imitate some semblance of medical treatment.

She was also the only person who could provide even the most basic care to those hit by arrows.

"Just hold on. It'll sting a bit."

As Qing spoke, she cleanly sliced off the arrow that had pierced through someone's shoulder.

"Argh!"

"There, you endured well. But could you please let go of my arm? There are others I need to attend to."

Among the twenty or so people, half were already dead, and half of the remainder would soon follow.

The Chief Escort was a wandering doctor who traveled to areas struck by terrible disasters or epidemics.

Therefore, the first lesson Qing learned was the order of treatment.

Those who would survive even if left alone, those who could be saved with treatment, those who were difficult to save even with treatment, and those who would die no matter what.

She had learned that to save as many lives as possible, sometimes it was necessary to abandon those who were dying.

In the end, only eight remained.

Fortunately, the most skilled among the escorts, Chief Escort Heo, had only suffered minor injuries.

Or maybe, it was only natural since he had the skills to dodge the incoming projectiles and only suffered minor injuries.

Four were teetering between life and death.

They tore up grain sacks and piled them onto the cargo cart to create makeshift beds for them, and two others who couldn't move were also placed on the cart.

One was lucky, having taken five arrows but miraculously avoided any fatal wounds.

"You should all head back for now. I understand the importance of the escort mission, but shouldn't human lives take priority? But what in the world is going on here? Those bastards, they weren't even bandits. Were they after the cargo?"

"This was a scheduled escort mission without any registered goods. Wasn't it just carrying grain?"

It was an escort mission, not a cargo run.

Grain was bulky and heavy, yet didn't bring much profit.

So, the routine escort mission, carried out periodically to circulate personnel between branches, had taken on the additional task of transporting grain.

Other than that, there were only letters being delivered through personal correspondence.

"I'll make those bastards pay for this. Don't worry about revenge and just head back. I'll slaughter every single one of them."

Then, Heo Seosan shook his head.

"Please don't. Those guys, they, um."

He then looked around cautiously, lowering his voice as if to prevent anyone from overhearing.

"I was once enlisted in the military. Those bastards are soldiers of the authorities."

"What?"

"It's a type of weapon called a Steel Penetration Crossbow. It can pierce steel from thirty paces away, and if used solely to harm people, its range exceeds a hundred paces. Arrows that can exert such force even without the infusion of True Qi…."

The type of weapon referred to as a crossbow was well-known in Qing's homeland as a Gak-gung.

"No, but why would they do that?"

"There must be something going on in the mountains."

"No, but if that's the case, they could have just told us to go back. Why would these bastards go as far as to impersonate bandits and harm people?"

"Shh. They must have their reasons for chasing people away like this. If rumors spread that the Yangsan Bandits are blocking mountain paths and killing passersby, no one will dare enter the mountains. They probably left a couple alive to spread the warning."

"No, but what kind of bastards do that?"

As Qing expressed her frustration, Heo Seosan suddenly bowed deeply to her.

"No, why, why are you doing this?"

"This Heo has received an immense favor from the Great One. Not only did you save my life, but you also saved the lives of my subordinates. Whenever you need me, please call for me. We are many who owe our lives to the Great One. I am untalented, but I wish to repay the debt with my life."

"Hey, stop that, and what's with the Great One? I'm not that old, you know? You're not in any condition to be doing that, so please get up. You should hurry back since there are people in urgent need of care."

The implication of ‘hurry back' was that she wasn't going back.

Heo Seosan's expression hardened.

"What do you intend to do, Benefactor? If you plan to confront them, I will assist-"

"No need. Take care of your subordinates. I'll take a look around, and if it seems too dangerous, I'll just get out of here. If I cut through the mountains, what would those bastards even know?"

"Then, please be careful."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The greatest weapon of the authorities was ‘rain'.

A rain of cannonballs to punish the enemies of the Emperor.

Or, during ceremonies, they could make it rain by shredding the most expensive paper into confetti.

Or, they could make it rain food, bestowing ‘kindness' upon the people.

When suppressing rebels, they could thoroughly soak the land with a rain of blood, exterminating even the nine degrees of familial relations1.

Except for actual rain made of water droplets, they could make anything rain down.

Actual rain was the will of the heavens, a destiny that humans could not dare to imitate.

(If there was a drought, it meant people just had to die.)

And a rain of arrows was also a specialty of the authorities.

Honestly, cannonballs were too heavy to be called rain.

Paper confetti was closer to falling flowers than rain.

However, arrows could be made to rain down in a manner that genuinely seemed plausible.

Records stated that when tens of thousands of arrows flew in unison during a volley, the densely packed arrows would darken the sky like a rain cloud, which wasn't one or two accounts.

Qing wasn't aware of this.

However, she had experienced the powerful steel arrows being fired, more than a hundred at a time.

It seemed like they shot one at a time and fled, probably because crossbows took a long time to reload.

There weren't a hundred of them hiding, but there sure were a lot of arrows, weren't there?

Although Qing tended to underestimate the primitive technology of ancient China, in reality, during the medieval era and earlier, China was at the forefront of human technological advancement.

Repeating Crossbows had already been fully developed more than a thousand years ago.

At any rate, here's a lesson from the bandits!

Identify the enemy's capabilities to the fullest, predict what they can do with those abilities, and prepare for it!

Qing had already seen the power of the arrows called Steel Penetration Crossbows and knew that they were fired in the hundreds.

Then, what should she do?

Avoid open areas, be cautious of any ridge that could provide cover, and always be mindful of the firing line.

Moreover, no matter how powerful, they were still just arrows.

They wouldn't be very effective if there were many obstacles.

That was why Qing was moving away from the mountain path and traversing the wild mountains instead.

And if things got dicey, she could just run away.

The escape Qing had in mind this time was different from the one during her time with the bandits.

Since she hadn't shouted out something like, ‘I am Ximen Qing of the Hubei Divine Maiden Sect', even if she ran away after killing as many of the bastards as possible, who would know who did it?

She didn't have to worry about trouble reaching the Divine Maiden Sect or about Seol Ri-rin or any of her other acquaintances getting caught up in it like she did back then with the bandits.

Thus, Qing cautiously advanced through the mountain terrain.

Her pointed toes silently dug into the dry leaves and were pulled out just as quietly.

This stealthy way of moving, even while treading through a sea of thickly piled fallen leaves, was the true potential of the Thief Under Heaven, who had now become the Female Thief Under Heaven.

Qing didn't make a sound, but the enemies did.

Rustle rustle. The sound of leaves being disturbed.

Not long after, two figures appeared, dressed in the savage attire of mountain bandits with thick furs.

What's with the fur clothes, though? It's not even that cold yet.

"Ugh, fuck, it's freezing. Hey, got any more of that weed?"

"Can't you just buy some?"

"Who's got money for that? Come on. Just give me one. I'll buy you a bunch later."

"Who's gonna roll a whole bunch of those? Why don't you help out a bit? You keep asking for one every time."

Qing narrowed her eyes.

Look at these bastards. Smoking weed?

When the law is so strict? You're all going to be executed. Beheaded. Chop chop.

Qing's law was whatever she felt like, but this time, she was actually right.

As the saying goes, even a broken clock is right twice a day. Also, even a blind squirrel finds a nut or two.

According to the law, soldiers who smoked weed during duty were indeed subject to execution by beheading.

It seemed like they had been smoking weed for a while, even carrying around those expensive lighters. They were utter addicts.

"Haaa, nice. It's really stretching me out. No matter how much weed I smoke, the stuff you roll is always the best. Is there some secret to it?"

"You won't smoke it even if I tell you, so why bother asking?"

"You little. If you're so smart, you should have enlisted earlier. Heh, hehe, hehe, right?"

"Hehe, that's right, hehehe……."

Laughing at passing leaves for no reason was a characteristic of those who smoked weed.

They were giggling over nothing and seemed completely out of it, so Qing didn't have to put in much effort.

Crack. One's head turned, his temple touching his shoulder.

However, the other one spoke in surprise.

"Oh, this bastard. Did he get so cold his neck turned? It turned a lot, didn't it? Hehehe, should I straighten it for you? He, hehet. Hey, wake up."

"Huh? Is that really weed? This guy's become a total retard."

"I'm telling you, this shit's amazing. I don't know what his hometown's secret is, but no matter how many other ones I smoke, none of them come close to this one."

"Oh. A hometown secret. That looks pretty strong. Did he soak it in opium or something?"

"Oh. That makes sense. So, you wanna try some of the esteemed one? I'm telling you, you're gonna love it. Hey, mister. We're in the middle of a mission, so let's just get this over with and go back to take a nice long rest, yeah? I have a three-room house in Beijing, you know? How's that sound?"

"Ooh. Owning a house in Beijing."

For reference, if we were to count by rooms, Qing's entire house was about the size of a booger, or half the size of a fingernail at best.

"So, you don't know the identity of this rebel?"

"If he's a rebel, then he's just a rebel. What identity is there for a rebel? The moment he becomes a rebel, he's just a rebel. Hmm."

It sounded strange, but it was true.

The moment someone became a rebel, they were just a rebel. Their previous identity disappeared and only the fact that they were a rebel who needed to die remained.

It seemed like the effects of the weed were wearing off.

Qing held out the joint that was still in the mouth of the corpse.

"Well, Officer, the weed seems to be wearing off. Here, have some more."

"Ah, right. There was still some left. Huuuu, ah, that's relaxing. But hey, cover your face. It's the rules, you know. Hehe, that's right, Cheonhwapung. Everyone's covering their faces these days, hehehe, isn't it funny? They think that if they cover their faces, they're all the most beautiful under the heavens, hehehe."

Hmm. It seems like Cheonhwapung is also trending in Beijing.

She had obtained a very useless piece of information.

In return, Qing slightly lifted her veil.

"Here you go."

"Gasp."

Then, the Officer inhaled deeply and suddenly knelt politely.

"Oh my, Heavenly Maiden, it is you, Heavenly Maiden."

Hmm. They come up with all sorts of things, don't they?

Qing played along for now.

"Indeed. I have descended from the heavens because I pitied you soldiers who follow the will of the heavens. I have come to provide solace."

"Oh, are you saying you will give it to me once?"

"However, I must know if you are truly a loyal soldier of the Emperor. Tell me everything you know about your mission. If I am satisfied, I will help you escape this cold."

"Hehehe, of course, my words? This elder is Tang Dongryang of the Northern Imperial Army's White Tiger Squad, and right now, we are here to……"

Tang Dongryang excitedly chattered on.

It wasn't very reliable since he was high on weed.

But it didn't matter. She could always cross-check with another guy later.

Qing listened to what Tang Dongryang had to say with some interest and, as promised, helped him escape the cold forever.

Now he would never feel cold again.

Then, Qing tilted her head.

Wait, no?

Don't ghosts usually say they're cold?

Is the underworld not heated?

It seems like the afterlife is very cold. In that case, did I fail to keep my promise? 