\chapter{Journey to Nanning (3)}

There was also one suspiciously weak one, which smelled nice but its purpose was unclear.

There was a bundle of paper. Oh, is this the map?

Since she was practically blind, she couldn't tell whether it was a banknote or a map just by looking at it.

She tried to move the contents to her own pouch, but the pouch was still damp.

She just put it back in and carried both pouches. Well, it seemed like she could depart again.

Then she felt utterly lost.

But, do I have to go in this state……?

I feel pain just from breathing……

But complaining wouldn't suddenly shorten the journey.

Nor could she stay in the middle of this harsh wilderness until she got better.

So, what could she do? She had to go. She had to go.

Qing tried to sigh, but, ow, she couldn't even sigh. Ouch.

When she tried to take a deep breath, her chest cavity expanded, causing her ribs to scream, the torn external oblique muscles to scream, the torn internal oblique muscles underneath to scream, the similarly torn transversus abdominis muscle underneath that to scream, the fluid-filled and sagging pleural membrane to scream, and the lower tendons, contracted from the pain, tightened around her pelvis, causing the cracked pelvis to scream as well.

But she couldn't just sit down and give up.

Let's go, I have to go…….

The direction was south.

Even though the sky was clouded (it was fog that was below her when she stood on the peaks of Zhangjiajie), she could still vaguely see a blurry light source in the white sky, so there was no problem figuring out the direction.

On her way, Qing saw Wang Cheolgun's half-burnt corpse in the pit created by the hammer's fall.

It seemed like no oil had been poured, so the body was more well-done on the outside and rare on the inside. But rather than that, her gaze was drawn to the huge two-handed hammer lying next to him.

It was just the right length to use as a walking stick, which was perfect since it was inconvenient to walk.

Upon lifting it, she found that it was much lighter than the Moonlight Sword (Greatsword, Size 10).

Although the weight was concentrated at the end, it seemed to weigh just under two kilograms.

Of course, that was the case.

There were not many weapons in the world that weighed two and a half kilograms.

Even if it was just under two kilograms, it was still quite heavy and impractical.

Among spiked clubs, it would be considered heavy enough to make one ask, ‘Are you sane to swing that around?'.

Moreover, the original spiked club wasn't even this heavy to begin with.

It had been modified to increase its weight.

Only after looking closely due to her impaired vision did Qing realize this fact.

Ah. This wasn't a two-handed hammer.

It was a spiked club.

The spikes were protruding from the half-broken hammerhead.

It seemed to have been modified into a hammer by pouring molten iron into a square mold with the spiked iron ball inside. However, since the bandits' ironworking skills were not that great, the hammerhead had broken.

And then, suddenly, her heart dropped.

Wow. This. I almost really died……..

So I just survived because I was lucky…….

They probably changed the spiked iron ball to a hammerhead to capture me alive.

If she had been hit by a flat hammerhead, the impact would have been evenly distributed, causing her side to burst.

But what if she had been hit by the head of a spiked club?

The sharp spikes would have pierced through, rupturing the peritoneum, and the impact would have been directly transferred to the internal organs.

Her organs would have been all ruptured and torn, leading to her death.

By now, she would have been pestering the ferryman of the Samdo River, asking if she was really dead at least three hundred times.

Of course, if it had been a spiked club instead of a hammer, Qing would have desperately tried to avoid it.

Only then did Qing deeply reflect.

Unrestrained Realm Masters were not so easy to deal with, and she was foolish to think she could somehow win.

Leaving behind the map, suspicious pills, or the great achievements of killing two Unrestrained Realm Masters and eradicating the bandits, this single moment of reflection was far more valuable.

Then, what should she have done?

She didn't have to burn down the stronghold so hastily. She could have just slowly backed off.

She could have engaged in guerrilla warfare in the Yuanjiajie, burning down strongholds one by one when the bastards seemed to loosen up a bit, thus establishing some discipline.

She could have decided to settle down and drag it out into a long-term battle, fighting in a more advantageous environment.

Or, though she would feel sorry towards future generations, she could have taken advantage of the dry winter season and just set the mountain on fire and fled.

Come to think of it, by the time future generations started tourism, wouldn't the trees have grown back?

However, it was originally so humid that it seemed like water was flowing under the ground.

She wasn't sure if she could have set a fire in the wet, primitive forest, even in winter.

While focusing on how she should have acted, Qing walked slowly, since it hurt to walk heavily.

Still, it seemed a bit better to have something to think about, even in pain.

Thus, after reflecting so intensely, she exited Yuanjiajie and found a village.

The name of the village located southwest of Zhangjiajie was Yuanjiajie.

In fact, the northwestern area of Tianzi Mountain and Tianmen Mountain was called Yangjiajie, the central and southwestern parts were called Yuanjiajie, and the eastern side was called Zhangjiajie. There were villages with the same name along the main roads.

This was because these names originally meant the land of the rebels who had hidden in this harsh, primitive forest.

The land where the traitorous Yangs lived, Yangjiajie.

The land where the traitorous Yuans lived, Yuanjiajie.

Likewise, the land where the traitorous Zhangs lived, Zhangjiajie.

Of course, even if they were called traitors, it was a story from ancient, primitive, ancient, ancient, ancient times, when dynasties had been overturned many times, so they weren't considered traitors anymore.

It was miscellaneous knowledge shared by the only inn's waiter in the lower village of Yuanjiajie.

It seemed like he wanted to brag about the village to the big spender who had emptied out all their precious ingredients today.

To be precise, it was the process of hitting on a peerless beauty who had descended into their village.

But, hitting on her as a waiter didn't make much of an impression.

Anyway, where else would there be an inn?

She paid with silver (since firewood was much more expensive in a small village) and soaked in a hot bath.

It was a good thing she had taken the top-quality scented soap left behind by the unnamed young lady as a keepsake.

She also had someone apply the Tang Clan's wound medicine thoroughly. Hmm, should she leave the wound exposed or wrap it up?

If left exposed, it hurt less when she was still, but it hurt terribly when she moved. If tightly wrapped, it hurt constantly even when she was still, but it was much easier to move.

But since there was no stable in a village with only one inn, she had to walk.

It was annoying and stung, but what could she do?

She also paid the village women some coins to wash the contents of her still-wet pouch, which stank of river water.

Originally, she would have done it herself, but now she couldn't even squat down, so she had no choice but to make the women do it.

Still, the women, who did laundry anyway, were happy to earn a few extra coins.

Qing was happy and the women were happy.

Thus, the uncivilized one, no longer a savage, put on her veil again, transforming back into a true Cheonhwa, and headed south.

She had no choice but to take a detour east because of her side, and it had already taken too much time.

Come to think of it, it seemed like she had her side burst because she was trying to go too fast.

This is why people say speeding is dangerous.

And so, south.

To reach Huaihua County, she had to cross the mountains on foot.

Still, it was better to tightly wrap up the wound.

Breathing deeply caused a refreshing pain? It felt like she could kind of? endure it? Walking wasn't so bad, was it?

Thus, upon reaching Huaihua along the Huai River, a smooth road stretched along the river all the way to the border of Guangxi Province.

Then, she could take a carriage to Tongdao County, the southernmost city of Hunan Province.

Then, a huge mountain range separating Hunan and Guangxi would block Qing's path.

But once she climbed over this, she would be connected to the highlands of Guangxi Province, which were relatively flat.

Qing's steps were fundamentally fast.

Her natural disposition was like that, and with the addition of superhuman physical abilities, she moved swiftly, to the extent that ordinary people without martial arts would fall behind, panting and gasping.

Even now, with her side burst, she was still fast.

If it wasn't for her side, she would have used Qinggong and flown, saying she was late.

Since her footwork with the Divine Footsteps Technique was inherently designed to minimize impact on the body, even with her injury…

However, her side had its own say in the matter.

With three layers of her flank muscles completely torn, it was a miracle that the wound hadn't festered or become infected, let alone healed.

This was because Qing's Constitution, the Poisonous Blood Constitution, provided complete immunity to secondary infections.

Qing knew this, so she pushed her body hard.

Didn't her body heal perfectly fine even after being torn and shredded multiple times, rolling around in contamination during her first year here?

So, as Qing limped along, advancing rapidly like someone who didn't know any better, she was traversing a mountain path when…

"Stop, halt!"

A large procession, which had been far ahead, gradually came closer. Just as they were about to meet, someone shouted, blocking Qing's way.

Qing frowned beneath her veil.

Ugh. I was matching my steps to the rhythm just right, too.

Because her steps were disturbed from the most pain-free rhythm, her naturally emerging voice was sharp.

"What is it?"

"……?"

The man was bewildered.

Then he asked-

"Didn't you follow us, Young Lady?"

"Oing. Me? Why? What are you that I would follow you or whatever?"

"……?"

"……?"

However, the porters who were listening in were feeling wronged.

Wasn't there a limping cripple with a limp, covering her face, chasing after them at a furious pace from down the mountain?

Moreover, from afar, it looked like she was threateningly tapping a massive, heavy-looking club with a large head on the ground. It was clear that this limping cripple, who also covered her face, was a formidable Master.

As such, all the porters had their hands on their swords, tensed and prepared for an encounter.

In truth, it was just a misunderstanding.

If it had been between martial artists of the Unorthodox Faction, a fight would have broken out immediately, but Qing was considered Orthodox and a porter was a porter.

So the misunderstanding was quickly resolved.

"Haha, I see, I apologize for the rudeness. I am Jang Hakseosan, the head of the Lakeshore Escort Agency."

"I'm Ximen Qing."

"Cheon Hwa Jeom!" "The Most Beautiful Under Heaven!" "Cheon Hwa Jeom!"

There seemed to be some strange noises mixed in there.

Anyway, this must be why repeating one's moniker is a courtesy in Jianghu. Everyone seemed to recognize her and welcomed her, which felt really good and pleasant.

"I never imagined I would meet Cheonhwageom Ximen Qing, Young Lady, in such a place. Are you perhaps heading to Guilin?"

"I'm going to Nanning."

"Ah. If it is not too urgent, would you mind accompanying us to Sanjiang?"

Qing thought for a moment. They had almost reached Guangxi Province anyway. Sanjiang was a city located just below the mountain. It wouldn't delay her schedule much.

And that much was not enough to give up the comfort gained from joining an escort group.

She could get plenty of food, snacks on top of that, and a comfortable ride in a carriage until they arrived, and even a small token of appreciation.

Why give that up just to save a few hours?

Thus, Qing took a seat on a cargo cart.

However, for some reason, everyone from the porters to the baggage handlers of the escort agency kept glancing at her.

It wouldn't pierce through her veil, though.

Since she was known as The Most Beautiful Under Heaven, or at least a strong contender for such a title, it was natural for them to be curious about her beauty.

But it wasn't like Qing would just reveal her face to satisfy their curiosity.

As Qing sat on the grain sacks in the cargo cart, ignoring everyone's hopes, Head Escort Jang approached and offered her a blanket.

"By the way, aren't you cold?"

Qing's attire was not suitable for winter.

With wide sleeves and ample pant legs fluttering even in early winter, it made even the onlookers feel cold.

Just looking at it made one feel like the cold wind was blowing right through.

However, as the owner of the Ice and Snow Divine Arts, Qing didn't feel cold.

She would have to lie down naked on the cold, frozen ground all night long in soaked clothes to feel cold.

But how could there be such a foolish and stupid idiot in this world who would lie naked on a cold, bare floor on a winter night while wearing wet clothes?

So, being dry and having the chilly wind blowing through her wasn't really that cold.

But there was no reason to refuse a warm blanket.

Just because she wasn't cold didn't mean she disliked warmth.

This Head Escort guy. He's very considerate.

"Ah. Thank you. I'm not particularly cold, but if it's offered, warmth is always welcome."

With a blanket wrapped around her, she felt warm and cozy, making her drowsy.

As Qing was dozing off…

"Halt!"

And the carriage stopped.

Ugh, what, what? I was just about to fall asleep.

Qing was thinking this as she wiped the drool from the corner of her mouth with her sleeve.

For reference, the porters had been marveling at how a Master could sleep soundly with a snore even on a cold day, with just a thin blanket wrapped around them.

Anyway, it seemed something had happened.

Having learned from the pain, Qing slowly and carefully raised herself.

Every morning, she had experienced a brief moment of unconsciousness due to the intense pain after suddenly getting up with vigor, at least three times before learning this modest posture.

As Qing stood on the carriage and looked ahead, she saw a group of people blocking the way. Even without clear vision, she could tell from the thick, furry clothes and the axes and large swords that they were bandits.

At that, the Head Escort stepped forward and performed a fist and palm salute.

"Heroes of the Green Forest, I see. We, the Lakeshore Escort Agency, have already paid the toll for passage-"

"Yeah, yeah, that's the toll for the Great Mountain Stronghold. Here, the great Taenokrim and the heroes of Liangshan Marsh have arrived, so you must show your sincerity separately."

Huh? Qing frowned.

Liangshan Marsh? Weren't they utterly crushed?

To be precise, wasn't it me who utterly crushed them?

Are these some remnants who managed to escape?

But how could the remnants of Liangshan Marsh, who fled from Zhangjiajie, be blocking my way here?

Did they run all the way here at full speed?

As Qing tilted her head in confusion…

The bandit's words continued.

"Hehe, this body is the leader of Liangshan Marsh, Do Wusam!"

At this, Qing was startled.

Otaeshik, no, Do Wusam has returned.

No, how?

Did someone pick up his head and reattach it or something? 