\chapter{Journey to Nanning (8)}

Subtle Waves Treading Steps was both a footwork technique and a
Formation.

It was based on the eight trigrams, the principles of Yin and Yang, and
the one hundred and eight directional methods that divided the thirty-six
directions of Heaven's Gate into three powers.

Thus, there were one thousand seven hundred and twenty-eight
possible paths, and the technique was to always take the safest route
among them.

Each time one calculated a single hexagram, one of the two hundred and
sixteen changes, an afterimage would increase.

And when Grand Completion was reached, the user would disappear
like a phantom along with eight afterimages.

Yan Pa found it hard to believe, even though she had seen it with her
own two eyes.

This foolish wench? Really?

"Ahem. You do have some tricks up your sleeve."

"I've always been quite skilled, you know?"

"Tsk tsk. That's the problem. A woman should know how to be shy when
praised, but you just get conceited. You're such a tomboy."

"Hehe."

Qing's secret weapon! Smiling without feeling offended!

Yan Pa sighed deeply at this.

"In the past, there was a strange and mysterious sect in Jianghu. It was
said that their martial arts were all capable of shattering mountains and
splitting the Yellow River, causing heaven and earth to tremble."

"A mysterious sect? What sect was it?"

"I don't know. It was said that they had a strange rule that anyone who
knew their sect's name must be killed, so the only people in the world
who knew the name of their sect and lived were themselves. Everyone
else died, so how could the name be known?"

"And?"

"Subtle Waves Treading Steps is a martial art of that mysterious sect.
You asked why your opponent appeared behind you earlier. It is said
that originally, Subtle Waves Treading Steps was created as a pair with a
martial art called the Northern Darkness Divine Arts. So, it is said that
even if one masters the changes, if they haven't learned the Divine
Arts, they cannot escape from the predetermined paths."

"Ah."

Northern Darkness Divine Arts. It seemed to be a martial art that was
given as a reward for achieving Ten Stars in all of the Ten Great
Demonic Arts Under Heaven.

"Then, Yan Pa was a member of that mysterious se-"

"Didn't I say I didn't know the name?"

"Right."

If Yan Pa was a member of the mysterious sect, she would have said she
couldn't tell instead of saying she didn't know, so she had already
revealed that she wasn't a member.

Or couldn't she just say she wasn't?

Perhaps the saying ‘appearances are a science' was indeed true.

"You have a very disgruntled expression, but what is a woman doing
without managing her expressions? Haah."

"So, how did you come to possess Subtle Waves Treading Steps?"

"It's just a secret manual of a ruined sect. It wouldn't be strange for
anyone to have it."

"Oing. It's ruined? Even though their martial arts are strong enough to
destroy the world?"

"It is said they fought among themselves over who would possess
which martial art and ended up annihilating each other. Hm. Isn't it
obvious they would fall, as they couldn't even reveal their own sect's
name? Only those who are not confident in themselves hide their
identities. Like this old woman and those bastards who serve His
Highness."

Qing recalled the Servants of Freedom.

Yan Pa was an old woman, there was a Dog, an Upper Thief who was
also a dog, and the Whore.

They were all villains whose numbers above their heads were red.

"Then, the Wheel-Turning Demonic Calamity is also from the
mysterious se-"

"That's not it. That was just a stroke of luck."

If she found Subtle Waves Treading Steps by chance and the WheelTurning Demonic Calamity was a stroke of luck, then what? Was she
someone who specialized in finding martial arts?

Did Yan Pa also use the Martial Arts Window?

However, there was a deep sense of regret and sorrow in her voice, so
Qing couldn't bring herself to pry any further and changed the subject
instead.

"So, what kind of Demonic Art is the Wheel-Turning Demonic
Calamity? I need to know to decide whether to learn it or not."

"It is a martial art like this. The Sword Force rotates like a wheel,
doubling its power. Um. Right. You said your eyes are bad, didn't you?"

Yan Pa manifested her Sword Force to demonstrate the Demonic Art,
but then she saw Qing's expression, which was just a frown and a ‘Um,
what the hell is that? I can't see anything at all', and sighed deeply.

"Can't you come a bit closer? I can't see very well right now."

"Ha, are you asking me to put my Sword Force right in front of your
eyes? You really don't know how dangerous that is, do you?"

"You're not going to attack me, are you?"

"Tsk. Here. Can you see it at this distance?"

"Just a little bit closer."

"It's dangerous, so just look from around there. This is what the
Wheel-Turning Demonic Calamity is."

It would be better if it was closer, but since she said it was dangerous,
she had no intention of pushing it.

Qing squinted her eyes and focused, and then she saw it. Yan Pa's hand
had Sword Force, and the shape was jagged, similar to a saw blade,
and then…

Ah. It's spinning!

The saw blade slowly began to rotate, gradually increasing in speed
until it created an afterimage.

Then, the Sword Force eventually thickened to the length of the saw
blade.

It was somehow a familiar mechanism for Qing.

This is… a chainsaw. Isn't it?

"Since it's a Force Art, you can change the properties of the Force as
you wish, right? You can use it with Sword Force, Saber Force, or
whatever."

"Isn't that obvious?"

A chainsaw, how could she resist this?

Qing swallowed her saliva.

"Are there any side effects? Since it's a Demonic Art, other than
becoming violent, I mean."

"Your eyes will get clouded. It's called the Wheel-Turning Eyes, and if
you use it in front of others, it's no different from shouting that you've
learned and are using the Wheel-Turning Demonic Calamity, one of
the Ten Great Demonic Arts Under Heaven."

"Oh, then. I can just use it on people I'm definitely going to kill?"

"What did you just say……?"

Yan Pa doubted her ears.

Was this something a female warrior of the Orthodox Faction should
say?

When using a Demonic Art, it was obvious that one would be found out.

So, just use it on those you'll definitely kill anyway, since you'll be
found out either way.

Of course, that wouldn't work.

When using a Demonic Art, one's murderous intent surged naturally
due to the influence of their emotions.

"If you wear a veil, it might be okay? Can you show me what the
Wheel-Turning Eyes look like?"

"Why are you shoving your face in here?"

"I can't see, though."

"You're a cheeky one, aren't you? Why are you so casual, shoving your
face in like this?"

"Well, hurry up."

Qing's eyes sparkled.

It was like the bright eyes of a dog looking at its owner holding a
food bowl.

Yan Pa made a disgusted face and activated the Sword Force of the
Wheel-Turning Demonic Calamity.

Then, three flames that appeared in her eyes began to slowly rotate,
chasing each other's tails.

"Ah. This. It's a very concerning shape. It's like a storm, a storm."

"If your emotions stir, it naturally appears, so don't say anything
dangerous like ‘murder and destroy evidence'. No, is that something a
Daoist should even say?"

"You said the world is dangerous, didn't you?"

"You never know when to stop, do you?"

"Hehe."

"Don't laugh, you brat. How can a woman be so loose with her laughter?
Ha, that's right. Now that I think about it, this is a big problem. Don't
smile carelessly. Don't show your teeth to anyone but your husband.
What are you going to do? Tsk tsk. Why are you keeping that open?
Can't you close it immediately?"

"Heuheuheut."

Qing closed her mouth as she was told and made a sound of laughter
only through her nose.

At that, Yan Pa was like, ‘What am I supposed to do with this
wench?', and felt the urge to hit her on the head, causing her WheelTurning Eyes to naturally activate and spin.

"It's late at night, so go in and sleep."

Yan Pa then added.

"Um, yes. His Highness might be feeling cold, so you should take care
of him. I know men and women should be treated differently, but this
time it can't be helped, so I'm asking you."

It was a request filled with personal ulterior motives.

But it didn't work.

"No. I'll stand guard tonight, so go in and rest up."

"Didn't you say you would examine the enemy camp tomorrow? You
need to rest."

"How tiring can it be for a Transcendent Realm Master to not sleep for
one day? Besides, Yan Pa's recovery comes first, and that's much more
helpful in serving His Highness, isn't it? You can't even walk properly
right now."

"What are you saying? This old woman is still perfectly fine. What do
you know, when you can't even see properly?"

"Eyyy, I heard the sound of you dragging your feet earlier. I'm fine, so
get some sleep, or if not, you can meditate. I'll stand guard, so don't
worry."

"Ahem. You're quite perceptive for someone who was just lying there.
How can this old woman speak when you're not even listening? This
is so frustrating. Tsk tsk."

Qing interpreted Yan Pa's grumbling.

‘Thank you. The young one should do it. Rest well.'

"Hmph."

And so, Yan Pa returned to the rocky crevice.

Lying down again with her arms and legs outstretched, Qing turned her
head to other topics instead of her frustrations.

Well, how can I not learn about a freakin' chainsaw?

It's not electricity, but since it's Qi, it's a Qi-saw?

Since it's Sword Force, is it a Force-saw?

It's rotating, so should I just call it a rotating saw?

I can't help but salivate just imagining the sensation of sawing through
something with it, the feeling of it vibrating through my hands.

But that's not the only reason.

It's not just because it looks cool, though it does look cool.

It's not just because I'm looking forward to how it'll feel in my hands,
though I am looking forward to it.

It's because there were strangely tough bastards.

Some kind of Grand Technique, with the character for ‘blood' in it.

I bet those fuckers also received something from those guys, didn't
they?

I thought I had split him in half, but it didn't even reach his nasal bone
and got stuck in his head, and when I tried to cut his arm, the Sword
Force got stuck on his shoulder bone.

It's no problem when dealing with one or two, but what if those
bastards come in hordes?

Qing had long since realized, in her first year, just how dangerous it
was for a weapon to get stuck and not come out.

So, since I had a stroke of luck and came across just the right martial
art, and since Master also told me to learn a Force Art…

Yan Pa also said it's no big deal to learn one Demonic Art since I already
know a Daoist martial art.

It's not like I'm going to go crazy just because I added one more when I
already know several.

It's not just because of the feeling in my hands.

It's necessary.

It's a very rational decision.

Besides, if I need the Northern Darkness Divine Arts later, this could be
preparation for that.

With that thought, the ominous color that did not exist in the world
spread in Qing's eyes.

Whether it was rational or not, Qing was currently on guard duty.

Leaving one person who didn't know martial arts and another who
could barely move due to her injuries.

At such a time, she shouldn't close her eyes, stretch her limbs, tremble,
foam at the mouth, and make strange noises, thus becoming completely
defenseless.

Of course, she might have just been thoughtless.

Thus, Ximen Qing.

Wheel-Turning Demonic Calamity, one of the Ten Great Demonic Arts
Under Heaven.

Six Stars.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was a tent set up on Namnyeong Mountain.

A man wearing silk robes, with a chicken's head valiantly rising from
the helmet on his head, a truly impressive sight.

"The beast? You still haven't found it?"

"Yes. We have not found it yet."

"Could it have escaped?"

"No. It could not have escaped. There are no issues with the
blockade."

"You just didn't notice it secretly escaping."

"They are the most elite warriors. They might not be able to handle one
hundred, but if a hundred of them gather, they can buy time against
even ten thousand, so they are strong soldiers."

"Hmph. Fine. It's just a rat in a jar anyway if it hasn't run away. How is
the construction of the firebreak going?"

"It has already been completed, but the geomancer says there are still
many dangerous areas, so additional work is underway."

At that, the man in the chicken-head helmet smiled a sinister smile.

"Hmm. Is that so? We can start the fire anytime, then? Shall we carry out
the arson at once?"

"If the fire spreads, not only the entire Namnyeong Mountain Range but
also Hunan, Guizhou, Guangxi, and Guangdong will be completely
engulfed in flames. The resulting loss of life will be well over tens of
thousands."

The man who answered, likely a general of the army judging from his
splendid armor, spoke thus.

However, the chicken-head man just scoffed.

"Hmph. His Imperial Majesty wishes to burn some of my property, so
what does it matter how many of those lowly peasants die? In the first
place, isn't it nothing more than some parasites burning to death,
squatting on the mountains of the heavens? Tens of thousands? In the
past, when Cao Cao performed the filial piety of human sacrifice in
Xuzhou, the number of people he buried alive was well over a hundred
thousand. Compared to that, it's nothing to make a fuss about just tens
of thousands of deaths."

This was the spirit of China.

In the past, even when Cao Cao performed the filial piety of human
sacrifice in Xuzhou, wasn't it said that it was nothing to make a fuss
about the massacre of Xuzhou's people when tens of millions died
during Dong Zhuo's tyranny?

In the distant future, the leaders of China would carry on this spirit,
saying that droughts, floods, and plagues were nothing to make a fuss
over when there were hundreds of millions of Chinese people.

"But-"

"Enough. That demonic old woman is said to have been seriously injured,
yes? So she probably can't even think of escaping for the time being.
Therefore, quickly finish the supplementary construction."
