\chapter{Journey to Nanning (6)}

According to the last words of Go Tangdongryang, the White Tiger, for this
rebel suppression, they had to dress up as bandits.

Qing thought to herself, ‘Why do we have to prepare our own costumes
for the operation?'

But in truth, in the primitive, uncivilized armies of ancient times, it was
common for soldiers to prepare their own supplies.

At any rate, Qing took off the fur coat of the macho man with the
crooked neck.

It was a high-quality item at a glance.

After taking off the macho man's fur coat, Qing sniffed it.

A temple-like scent wafted up, so even though he was a fake, he was a
Daoist after all, so it brought a bit of comfort to Qing's heart.

Wow, this is really well-scented.

However, it was a bit ridiculous.

What kind of bandit in the world would wear such a fine raccoon fur coat
with incense infused in it?

What in the world do they think bandits are?

Do they have too much of a fantasy about bandits?

And the pinnacle of it all was the hat.

Wasn't a sable fur hat considered the most luxurious hat one could
wear in winter?

Qing put it on and loosened the string on the folded part, completely
covering her face except for her eyes.

And then, the hat of Baekho Tang Dongryang, who had already departed
this world, was also a luxury item.

This was because fur hats in winter were a means for soldiers to show
off their wealth, even if not pretending to be bandits.

That hat is also really nice.

Since he's already in the afterlife, where the underfloor heating is so
warm it's practically burning him, he wouldn't need a hat, would he?

And although the coat wasn't as nice as this one, it was still a luxury
item.

Hmm, should I just give it to Jangmyeong?

In the end, Qing diligently packed Baekho Tang Dongryang's coat and hat
into her travel bag, stuffing them in with all her might using the strength
of a Hercules.

As Qing dressed up as a bandit, she started to resemble a professional
bandit.

After roughly burying the body under fallen leaves, Qing started
climbing the mountain again.

Despite his high status, the White Tiger was just a low-ranking
member in this rebel suppression, right?

If a low-ranking member was wearing such a nice coat and hat, what
about the higher-ups?

Should I try to get a few winter clothes while I'm at it?

And so, the sun set.

Qing's coat had become even more luxurious, and she was now wearing
the highest-grade white sable fur hat.

The unit price of her winter clothes had risen vertically, but in fact,
there was no real gain.

Come to arrest the rebels, but when you see a suspicious person in the
mountains, send a signal immediately.

However, there was bizarrely little information about suspicious people,
except that they were pale-faced scholars, so it would be obvious at a
glance.

Apart from that, the scale of the mobilized troops was unusual.

They were from different general's offices, so the exact number was
unknown, but there were five offices that had dispatched one or two
hundred soldiers each, and she heard that Embroidered Uniform
Guards were seen, and that unpleasant eunuchs (she really said it like
this) were roaming around.

The Steel Armored Soldiers were not mobilized for the search and had
set up camp separately, and only the staff officers knew where they
were ambushed.

Hearing the words Embroidered Uniform Guards, she suddenly
remembered what happened at the Tang Clan.

That fake Unrestrained Realm Master who ate Grandfather's special
vitality supplement and shook his waist in the air, violating the world,
was really tough.

Didn't something disastrous happen around lunch earlier where some
particularly tough guys were involved?

As she thought about this, she gnashed her teeth.

These fuckers, just how rotten is this country's government?

She had already heard that the current Emperor was grinding his teeth,
saying he would kill all those Wulin bastards.

It's fine to say that the government hates private armed groups.

But what's with killing passersby just because they're there to catch
rebels?

If it were an official government action, everyone would have
cooperated without complaint. Well, maybe they would have offered
some silver first, but if that didn't work, they would have grumbled
about why they weren't getting their silver back, but still would have
turned around.

But their choice was to kill and silence.

And they even cowardly disguised themselves as bandits.

That old man, the Celestial Martial Emperor, had a good reason to storm
the Imperial Palace and grab the Emperor by the collar.

But he only grabbed the collar. If it were me, I would have separated
the collar from the neck bone.

That's a terrifying thought, of course, because Qing wasn't from the
Zhongyuan.

Even the Celestial Martial Emperor, the epitome of radicalism, only
intended to teach the Emperor a lesson and never even thought of
committing the outrageous and dreadful crime of regicide.

This was why Qing was wandering at night.

They're doing it in secret because they can't be upfront about it.

Considering what happened to the Tang Clan, it was no ordinary matter
to have mobilized even those tough bastards.

So, she couldn't just ignore it.

It's cowardly and wrong.

If she hadn't known, she might have ignored it, but she couldn't pretend
not to know.

Besides, there were those who had died unjustly, and there must have
been others before them.

At least as someone wearing a Daoist uniform, she should offer some
solace to those wronged souls.

Qing steeled her resolve.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The winter in the Nӑn Lіng2 Mountains was not as harsh as that in other
mountainous regions of Zhongyuan.

However, for the people of Sichuan, it was still a severe cold.

It was so cold that in the history of Sichuan, there had never been a
record of water freezing, even in the coldest winters.

Thus, two people from Sichuan were hiding in a rocky crevice somewhere
in the foothills of the Nӑn Lіng Mountains, and the cold of the winter
night seemed to seep into their very bones.

One person was simply cold.

However, the other person, who was originally a Master and should not
have felt cold, trembled uncontrollably because when a person's
muscles below the skin are exposed and blood leaks out, even a Master
cannot help but feel cold.

"Your Highness, please leave me. Just leave me and go."

"What nonsense are you talking about?"

"Please, I implore you with all my heart-"

She was an old woman with completely white hair, yet not many
wrinkles.

However, there was blood around her mouth, her complexion was pale,
and there were dark shadows under her eyes, so she looked quite ill.

At that, the young man snorted.

"Hmph. What nonsense. What can a mere bookworm, who can't do
anything in these mountains, do alone? You should have taught me how
to survive in the mountains or something if you had anticipated this
situation. You always fussed over me, not letting even a drop of water
touch me. So of course, I don't know how to do anything by myself."

"Your Highness, please."

"Just get better quickly. If we had at least one sturdy guard, we could
escape. If I leave alone, even if those outrageous bastards don't get
me, I'll probably die wandering the mountains. You know how
treacherous these mountains can be."

"Your Highness, please. Just run north. While I can still cause a
disturbance, while I'm still useful, please use me. Please, don't let me
die in vain-"

"Why are you talking about dying? If you're going to die, you should
think about getting better with all your might. Hmm. Here's some water,
ah. Oh dear. It's empty."

"Your Highness. This old servant's lifelong wish is-"

"Enough with that talk about your lifelong wish. It's always your lifelong
wish. If you have so many of them, tsk."

"Your Highness, Your Highness! It's dangerous, it's dangerous!"

The old woman called out to the Prince urgently, but since they were
surrounded by enemies, she couldn't raise her voice.

However, the Prince just clicked his tongue and headed out of the
crevice.

Having come out to fetch water, the Prince found that it was much
darker than he had expected, so he couldn't take a single step carelessly.

He had seen a small stream, or rather, a trickle of water, while coming
up.

So he had ventured out confidently, but upon coming out, he realized
that the crevice, illuminated by the moonlight, was actually a bright
place.

In fact, a prince never had to climb a mountain on his own feet.

He would ride in a carriage, or a sedan, or a horse, or if none of those
were available, he would, of course, be carried on the back of a servant.
It was a precious body that would never have to walk on its own, after
all.

So, what would Prince Deokhyun know about descending a pathless
slope on a dark night?

He carefully stepped and pressed down, checking for any slipperiness
or fragile ground or rocks.

"Oof."

Crunch!

Prince Deokhyun slid down the slope, banging his knee on a stump,
causing him to crumple and roll down, hitting his shoulder on a rock
with a thud before falling three fathoms into a ditch.

Fortunately, he landed in a pile of fallen leaves, so he didn't get hurt
too badly.

"Ugh."

Prince Deokhyun tried to get up but couldn't, so he just squirmed among
the leaves.

His knee seemed to be busted, and his shoulder felt as if Guan Yu, who
had been shot by an arrow, would have felt this kind of pain.

Not even daring to get up due to the excruciating pain, Prince Deokhyun
just buried his body in the soft leaves and waited for the pain to subside.

"Cough."

Prince Deokhyun turned on his back and stretched out.

Through the bare branches, where the leaves had all fallen off, the
bright half-moon shone.

Suddenly, he found his situation ridiculous and pathetic.

As a prince, he couldn't do anything on his own, so he just lay there
pathetically, unable to even fetch a container of water.

It was then.

Suddenly, a shadow blocked the moon, and a cold chill ran down his
neck.

The coldness unique to metal. As a blade touched his neck, fear surged,
his heart seemed to drop to the ground before pounding as if it would
burst, and his limbs felt cold and numb, tingling and aching.

"What the hell is this? Why are you rolling around under the moonlight?
You got perfectly good feet, yet you don't even use them?"

It was a woman's voice, completely unexpected.

Her tone was beautiful and her pronunciation was clear, making it a
pleasing voice to hear.

"I am, well, an, a herb, a herbalist."

"A herbalist? A herbalist who talks like that?"

"A herbalist, I am."

"I've never seen a herbalist dressed in silk in all my life. Nor a herbalist
who rolls around clumsily in the mountains."

"Ahem, well, I just got lost because I could not discern the earth in the
darkness of the night."

"If you're going to pretend to be a herbalist, you should do it properly.
What kind of herbalist uses such literary expressions? Were you
preparing for the civil service exam and switched to being a herbalist
due to financial difficulties?"

"Ah, that's right. You guessed it."

"You sound like a very high-ranking person, though?"

"No. I, uh, she, no, this one is not a high-ranking person. Not at all."

"You just made a really stupid sound. Eh. Go? She?"

Oops. It was a slip of the tongue that came from habit.

In fact, with a blade at his throat, it would be more impressive if there
was no slip of the tongue.

Suddenly, the woman grabbed his collar and lifted him up with
unimaginable brute force, dangling him in the air.

He was gasping for breath when-

Suddenly, the woman pulled his collar close to her face, almost
touching her nose, or more precisely, the mouth covering that was
wrapped around the lower half of her face.

Then, she squinted her pretty eyes, which seemed strangely familiar,
and looked up and down, left and right, scrutinizing his face thoroughly.

From Prince Deokhyun's perspective, being held by the collar and
swayed around was quite an unpleasant experience.

Moreover, wasn't this woman being rather rude?

If she wanted to examine him, she should move her own eyes, why was
she shaking his body around?

Then suddenly, the woman's eyes widened-

"Huh? Freedom3? Is that you, Freedom?"

"Freedom? How dare you call me by that name."

The pseudonym ‘Freedom' was made up on the spot.

And there was only one person in the world he had allowed to call him
that.

"Is that you, Ximen Qing, my friend?"

"Wow, it is Freedom. Wow, mind blown. What the hell? What are the
odds of seeing you in a place like this? Wait, why is a prince rolling
around under the moonlight? Are you hurt anywhere?"

Only then did Qing put Freedom down, and started tapping and knocking
away the dirt and leaves stuck to his body.

As she patted his butt, Freedom turned red, feeling embarrassed, and
said, ‘No, what kind of woman is so casual, this is really strange and
outrageous'.

"Ah. That's right. Were you the traitor, Freedom?"

"Traitor? What an outrageous thing to say."

"Change your tone. Should I treat you like a prince?"

At this, Freedom smiled.

"Well, that's because my friend is making outrageous claims. But you,
uh, never mind. This isn't the time."

The smile disappeared, and Freedom grabbed Qing with an urgent
expression.

"You must help me. Yeon Pa is seriously injured, and her condition
seems poor. We need to get her to a physician right away, but as an
ignorant high-born, I do not know the way through these mountains. So
I'm asking you, can you take her to a physician?" 