\chapter{Journey to Nanning (7)}

"Go inside and get some rest. You must be tired. It's important to conserve your energy."

"Hmm. You might be right."

Jiyu nodded in agreement.

This left Qing at a loss for words.

She had planned to persuade him, arguing that he needed to rest to build up his strength so he wouldn't become a burden. But she hadn't expected him to agree so readily.

Upon entering the crevice, Yeon Pa was seen deeply immersed in meditative breathing.

His face, which had appeared blurry as if it were ten different faces overlapping, now looked much closer to a normal person's complexion.

Lying down a good distance away so as not to disturb him, Jiyu suddenly asked as if a thought had occurred to him.

"Don't people usually stand watch or something?"

"I'll wake you when it's your turn, so go to sleep for now."

"I understand."

What do you mean you understand?

Qing burst into laughter.

It seemed Jiyu was very tired, as he soon fell into a deep sleep, judging by the soft, rhythmic sounds coming from him.

He must have been sleeping on luxurious beds all his life. To think he could fall asleep so easily on the rough ground, even if it were cushioned with fallen leaves. It really showed how tired he must be.

But then again, with two layers of thick fur coats, it must be quite comfortable, huh?

Qing went outside and lay down on the ground.

After all, if she had to stand guard, there was no need to sit or stand uncomfortably.

This was a common excuse used by those who would doze off anywhere, regardless of time or place.

The moon was so bright tonight.

But is that the full moon? It doesn't seem like the right time for a full moon, so maybe it's not, but…

Thinking back, when they left Zhangjiajie, everything was so blurry that she could barely see. But now, things had improved significantly.

But is this right?

Isn't it that once your eyes are damaged, they're done for?

Ever since the injury, her eyes had been tingling, and she felt like they were recovering, so she wasn't too worried.

It was that same tingling sensation from back when her nerves were damaged during her time with the Demonic Cult, a unique signal that seemed to say, ‘Hey, body owner, don't worry. The nerves are healing diligently, so relax and go about your business.'

But still, do eyes actually heal like this?

But if eyes could heal, it seems like there wouldn't be a need for glasses, or procedures to reshape the eyeball or attach a lens.

If only I had read medical books instead of studying Korean history…

Was this a natural healing process, or was it due to her constitution, her high health stats, or perhaps a health bar or injury gauge gradually filling up?

Is it okay to just let it be, thinking everything will be fine?

But while malice might not have a reason, kindness often came with a price tag.

Qing opened the shimmering quest window.

She suspected it might be related to that whole Yellow Dragon Struggle thing from before.

But since the text was all blurred and unreadable, it remained just a guess.

She wanted to read it, especially since it was a quest related to her friend, but whenever she tried to focus on it, the window would either move away or come closer, always maintaining its distance, making it impossible to read.

What the hell? The convenience features here are so messed up.

What if I go blind? Will it even read it out loud for me?

Or what, will new eyeballs just sprout out even if they burst?

It wasn't a puzzle that could be solved by pondering, unlike a math problem.

And Qing couldn't even solve math problems.

After all, she had long given up on math.

Just as Qing was starting to feel frustrated thinking about the unsolvable problem…

There was a rustling sound of footsteps.

If it were Jiyu, the sound would be more like a loud, disruptive ‘crunch-crunch' of leaves being trampled, so it wasn't him.

Then, there was only one person it could be.

"Are you feeling any better?"

"To think a woman would lie sprawled out on the ground like a commoner, without any shame. I thought you were fast asleep, taking over the watch."

"Well, it's not like I can see clearly anyway. I'm focusing hard with my ears, though."

"Hmm, yes. That is right. What safety is there to be lax? That is not right. Indeed. Not right at all. Yes. Not right."

Yeon Pa kept repeating that it wasn't right.

In response, Qing chuckled and said.

"Thank you, by the way. It would be a waste not to use the medical skills I learned, and I was worried they might get rusty."

She was just circling around because she was too embarrassed to say thank you. She looked like a spiteful mother-in-law. Is this why they say that your appearance is linked to your personality?

Well, it has accumulated as much data as the history of Zhongyuan, after all.

"Hmph. To think a woman would be quick-witted. Well, that one thing is quite to my liking. Good. A woman should be quick-witted."

Then, a faint laugh.

"Yes. It seems that fate is indeed fate. To think a woman would be so unruly and wild like a commoner. I thought she would be utterly useless."

"What, so a man can be unruly and wild then?"

"Can a man escape his innate nobility, no matter what he does? He will forever remain a commoner, leaving behind a common name. So what fault is there in a commoner acting like one? But women are different."

In other words, men would always remain common, but women could rise in status. In Qing's homeworld, there was even a specific term for this: ‘Marriage Upgrade'.

Qing was on the fence about this.

Is this something Master would be furious about or not?

"Especially you, being in the position you are in. Always keep in mind to maintain a tidy appearance and act like an elegant noblewoman."

Always be tidy. Elegant and beautiful. Maintain the dignity of a female martial artist of Jianghu.

That's what Master used to say all the time… but.

Come to think of it, she hasn't been saying that lately?

Did she give up?

Anyway, Qing's voice was full of grievance.

"But why do I have to be even more so?"

"Hmph. What do you mean, why? Don't you have any wits about you at all? What use is a woman with no wits? Tsk tsk."

"You just said you liked it a moment ago……"

"Hmph. Don't you act as the close friend of His Highness? It is said that one can judge a person's character by their friends, so if you are unruly, wouldn't that be a disgrace to His Highness?"

"Hmm, I'll try my best."

At that, Yeon Pa nodded.

"At least you don't sound hateful when you speak."

Then, she finally brought up the main point.

"You should depart with His Highness. This old woman will create as much of a disturbance as possible, so it shouldn't be too difficult for you. But you must take great care not to let even a hair on his head be harmed."

"I'll have to hear Jiyu's opinion on that too."

"Tsk. When an elder speaks, you should listen."

To that, Qing shook her head.

"Leaving him behind like that would only hurt Jiyu's feelings more. He hasn't even done anything yet, and you're already telling him to run?"

"I have long prepared myself to serve such a noble person. It is what a commoner should naturally do."

At that, Qing's expression hardened.

"Why do you keep saying common and noble? Do those with royal blood have veins of gold or something?"

"Hah. You're really showing your true colors now. Of course, anyone in the world can tell what is more precious between gold and straw. Are you not going to be a traitor? It's just inevitable that a commoner makes common remarks."

"If there's an urgent need to start a fire, what's the point of having thousands of taels of gold? The tinder to start the fire would be more precious at that moment. And if we're talking about bloodlines, I could be a princess too if I wanted to."

"Hah, now you're going around telling everyone that you're going to be a traitor?"

"Even now, aren't you trying to commit treason by holding soldiers?"

At that, Yeon Pa's forehead bulged with a vein.

And her neck felt so stiff that it seemed like she would burst a blood vessel if she talked any further.

But she sighed deeply at the following words.

"Anyway, you know. Jiyu would probably value you more than gold, so don't say things like that."

"You're too naive, woman. You're still too green. How dangerous do you think the world is?"

If she becomes any more worldly, she'll turn into a Killing Star, though.

But Yeon Pa didn't know that.

She just thought the woman was not harsh enough and too soft. She needs to have more venom in her heart if she wants to stay by His Highness's side.

But on the other hand, she was also pleased. She seemed to be a good match for His Highness.

She was eating all the side dishes before the main course had even arrived.

In Qing's homeworld, it was like downing a bowl of kimchi soup first.

"Anyway, um, do you know how many of them have come? I asked a few I caught, and they all said they were from different places. When I added it up, it was over a thousand."

"I'm sure the Iron Sword Bastards have come as well. To think they would pull out the Northern Army to this place. I wonder who's guarding the North."

At that, Qing carefully asked.

"Um… What about the others?"

"The Embroidered Uniform Guards, the Eastern Depot, and all sorts of blockades, with iron pellets raining down from all directions. This old woman has some tricks up her sleeve, so I'm still breathing. But as for the others, they're probably all dead. Anyway, do you have any bright ideas?"

"Not yet. Let's wait and see for a few days. Yeon Pa, you should be able to move more comfortably in three or four days too. From what I've seen, their military discipline is a mess, and their searches are half-hearted. They don't seem very dedicated. I'm thinking of following them secretly tomorrow."

"I'll watch and see, but if I think you're being too reckless, I'll shout and create a disturbance right away. If they all come rushing in, you'll have no choice but to run away with His Highness, right?"

"Why are you threatening me like that?"

If things went south, she was saying she'd draw attention and die.

She was acting like an old woman desperate to die.

Seeing Qing's expression, Yeon Pa chuckled as if she were dying, and then she took out another Secret Manual from her bosom.

"Ah, right. Take this too."

Qing could tell just by receiving it with her hands.

The Martial Arts Window was flickering brightly, signaling the arrival of a new martial art.

Qing held the manual close to her nose and struggled to read it out loud, letter by letter.

"R, Ro, ta, ting, Hea, ven, De, mon, ic, Ar, t. Huh? Isn't this one of the Ten Great Demonic Arts Under Heaven?"

"Do you know why the terms ‘noble' and ‘common' are important? If a commoner learns it, it's a vicious Demonic Art. But if a noble person learns it, it transforms into a mystical Divine Art. That's the way of the world. Anyway, since you're going to die soon, you can have it. Decide whether to learn it or not on your own."

"Why are you giving me Demonic Arts out of the blue?"

"If a woman who has reached the Transcendent Realm with Daoist martial arts learns a Demonic Art, do you think she'll be consumed by its nature? Even if it's vicious, there aren't many Qi Cultivation Techniques in the world as powerful as that. And didn't I tell you? A woman who is to become noble can learn some Demonic Arts."

Qi Cultivation Techniques.

They were techniques that dealt with Force Energy in earnest.

It referred to unique skills that either changed the nature of Force Energy altogether or utilized it in extraordinary ways.

Among the Qi Cultivation Techniques that Qing had learned were the Heavenly Demon's Ray, which fired rays of Force Energy from her fingertips, and the Heavenly Demon's Finger.

What the hell? You just gave me a Demonic Art?

What does this mean?

Of course, it meant that the old woman was fully prepared to die.

It was an asset liquidation by someone facing death.

In other words, it meant something like this.

If things got really desperate, she was asking Qing to abandon her.

So Qing accepted the Secret Manual.

It was an answer that she would do so if it came down to it.

After all, as a martial artist, Qing wasn't naive enough to think that everything could be resolved through sheer determination and grit, as hopeful stories often portrayed.

But what does she mean by a woman who is to become noble?

At that, Yeon Pa smiled.

"Yes. And I gave you the Ethereal Steps too, didn't I? How was it? It's a completely messed up martial art, isn't it?"

"Um. It is a bit like that."

Qing answered, thinking that it was only useful for running away since it always made her appear behind the enemy.

But Yeon Pa seemed to have taken the answer differently.

"How could they even make a martial art that a person is supposed to learn? How much blood was spilled because of that single, useless Secret Manual? So always be careful."

"Huh? Was it originally impossible to learn?"

"Hmph. Why, did you learn it or something? Even if you can imitate it to some extent, it's not-"

Yeon Pa's words suddenly stopped.

Qing's figure had multiplied into eight, each taking a different path as they scattered in all eight directions.

"Um. I don't really get why it makes me appear behind the enemy, though?"

At the sound coming from behind her, Yeon Pa rubbed her eyes.

What did I just see? 