\chapter{Journey to Nanning (6)}

"Yan Pa?"

Qing tried to recall what she knew about Yan Pa.

She definitely remembered her as an old woman with a very vicious impression. She was the type to throw water at her daughter-in-law, throw tea, overturn the dinner table, throw soup, throw out the laundry, and throw lye water.

And she gave her the Ethereal Steps.

The Ethereal Steps was a top-tier secret technique that had already saved Qing's life several times.

Even her Master, who usually said, ‘Oh, you learned that? Then keep it to yourself,' when she learned something new, had asked if the other disciples could learn it too. It was a life-saving technique.

Well, what about it?

When Yan Pa gave her the Ethereal Steps manual, it wasn't like she said, ‘Hey, there's nothing like this in your sect, is there? Keep it to yourself, okay?'

"Yes. She's like a raging inferno right now. Let me ask you this favor."

"Well, let me see. I'm practically a doctor. I've never been called a quack wherever I went."

"You learned medicine? You, my friend?"

Zi Yu's expression was a bit doubtful, but from Qing's perspective, she just had a pale, almost sickly appearance anyway.

"There's no time to waste. Let's hurry."

"Ah. Yes. However, I was on my way to fetch some drinking water. I did find a stream nearby."

"Ah. You can't just drink any water you find in the mountains because you're thirsty. You don't know which water is safe to drink."

Zi Yu hesitated at that.

"Do you mean there might be poison in the water?"

"Well, something like that. If you boil it, it's usually fine, so just keep that in mind. And I have water with me."

"It looked as clear as clean water, though."

"Of course, you shouldn't drink it if it looks dirty. Anyway, where's Yan Pa?"

"I've set up a shelter in a crevice up there."

"Her speech… If this keeps up, she might start speaking like an old man soon. Also, we can't just roll down when descending, so how did you expect to climb back up? I guess I have no choice but to carry you, huh?"

"Ahem. I would appreciate it if you could, just this once, since Yan Pa's condition isn't good."

Zi Yu was also someone who had experience in being carried and held.

Not to the extent of an expert like Qing, though.

So he stretched out his arms as if telling her to hurry up and carry him, but Qing just picked him up and placed him on her shoulder.

"Mm. Friend. Is this how one usually carries a person?"

"I'd like to carry you on my back, but if I do that, I'm confident I'll pass out within two steps because of the wound on my left side."

When a person was carried on someone's back, their legs would inevitably wrap around the carrier's waist.

And the carried person also had to tighten their legs to reduce the burden on the one carrying them.

"You're hurt, friend?"

"It's been about half a month? Just hold onto that bag tightly. Don't go spilling your words and biting your tongue."

Qing hoisted Zi Yu over her shoulder and started climbing the mountain.

Following the path where a person could roll down, they soon found a crevice between the rocks.

As soon as Qing entered the crevice, Yan Pa, with a startled expression, looked at the stranger who had suddenly appeared carrying the prince on her shoulder.

The Soul Flames flickered in Yan Pa's eyes.

Three tailed flames spun around, chasing each other. It was the Wheel-Turning Eye of the Wheel-Turning Hell, one of the Ten Great Demonic Arts Under Heaven.

But that was only for a moment, as it soon disappeared upon hearing the clear voice that came from the stranger's mouth.

"Yan Pa, how are you?"

"Mm? Who is this woman?"

"It's me, Ximen Qing. Do you remember? The Ethereal Steps you gave me last time has been very useful. Thank you."

Yan Pa let out a deep sigh of relief.

As the relief came and went, the Wheel-Turning Eye flickered again at that irreverent appearance.

"How dare you carry His Highness like a sack of luggage? Do you not know decorum, you wench? Put him down at once!"

"Ah. Yes."

And then more nagging.

"No, you wench, if you saw that His Highness was trembling, shouldn't you have taken off your outer garment to cover him? I heard that you reached the Transcendent Realm, but how could you, a Master who could be presented anywhere, wear only fur while he suffers?"

Ah. I didn't think of that.

It's not like if I'm not cold, others won't be cold either.

"Ah. Just a moment."

Qing unpacked her bulging bag and took out a compressed outer garment.

"Here, put this on. Turn it inside out so the fur is on the inside."

"Yan Pa needs it more urgently than I do. You should put it on Yan Pa first-"

"Your Highness, what are you saying? You must preserve your precious body. Here, Ximen brat, hurry up and put it on him. He's someone who can't even dress himself."

Didn't Zi Yu say, as soon as he saw Qing, that Yan Pa was seriously ill and asked her to take Yan Pa to a doctor?

Meanwhile, as soon as she saw Qing, Yan Pa nagged her to take off her warm fur coat.

Hmm. I miss Gramps and Sister……

"It's okay. I have more here. Here, Zi Yu, put on another layer, this time with the fur on the outside. There are enough coats for Yan Pa too."

Qing took out more super-compressed coats from her bag.

She had packed them, thinking it would be good to leave them at the Divine Maiden Sect for the disciples to use when purchasing goods or going out in the winter.

The two were bewildered as they watched her.

What? Why are so many coats coming out of her bag? Is there nothing in her bag but coats?

"Wench. I-Is the Divine Maiden Sect… in dire straits? Are you going around selling coats?"

"Huh? The Divine Maiden Sect is richer than ever."

Her Imperial Majesty had granted them all the nearby land as a ritual fee, hadn't she?

It was a very self-serving grant, as the Empress was also a member of the Imperial Family. One could say she was treating the nation's assets as her own.

Or perhaps, since she had sent it to the princess, the owner was similar.

Thanks to this, the already wealthy Divine Maiden Sect was now openly a super-rich sect.

Of course, their frugal and austere lifestyle wouldn't change.

"Tsk tsk. I thought you were an unrefined Daoist, but it turns out you were kicked out? Why are you going around selling coats when you have such high martial arts? If that's the case, you should seek refuge in the palace. Yes, that's a good idea."

"Ahjumma, I'm not selling coats, okay? Anyway, I'll take a look at your wounds. Zi Yu, you can go out now."

"Is it her? Even though her vision is poor due to her age? I can help you by your side."

"What's the point if you're going to keep your eyes closed? You want to see Yan Pa's bare skin?"

"Ah. I see. Indeed."

"You wench, where in the world is there a law that states His Highness should avoid his subjects? It is the law that demands the lowly avoid such situations!"

"I'm asking you to leave."

Zi Yu cut off Yan Pa's nagging and quickly ran out of the crevice.

Yan Pa just huffed with a dissatisfied expression.

Qing checked her pulse.

Wow, what the fuck. She's practically on fire.

I thought she was fine because she seemed so energetic.

There was an arrow in her thigh, one in her shoulder, and one in her forearm. And there were several large and small lacerations.

Among them, some wounds were already oozing pus, a sign that they were starting to rot from the inside.

It was a miracle that she was still alive with only her torso intact. If it had been otherwise, she would have long since died or fallen into a critical state.

"My goodness, does this not hurt? How can you be in your right mind?"

"Hmph. If a lowly person is to groan, should His Highness just stand by and do nothing? Anyway, did you say you knew medicine? I haven't heard that before."

"I learned it afterward. From a doctor called the Wandering Physician, who is said to have the biggest mouth."

"That busybody quack, you mean."

"It's not busybodying, it's admirable. Anyway, do you have any numbing medicine, by any chance? No? You would have taken it already if you had, huh. Just hold onto this. It's going to hurt."

Qing handed Yan Pa a fur scarf to bite on.

But, Ptui.

"I've endured until now just fine. There's no need."

Qing now carried various medical tools with her, and her eyes had developed to the point where she could spot precious medicinal herbs and collect them as she passed by.

She had packed them just in case something like this might happen (precious medicinal herbs were expensive), and it seemed that preparing in advance had paid off.

Of all the people, who would have expected this wench to be so thoroughly prepared?

She sliced, squeezed, pulled, and sewed.

As Qing's face was almost touching the wounds, Yan Pa asked with a suspicious tone.

"You wench, your eyes…"

"They're a bit damaged, so it's hard to see. But I can see if I get close, so don't worry-"

"Who's worried about that? You wild boar-like wench, not knowing how precious your body is. How did you end up with such ruined eyes? Are you okay? Will you be blind forever?"

"Hehe, it's nothing. It'll get better soon. Maybe half a month?"

Her tone was harsh, but she was ultimately worried about Qing, who smiled widely.

"Don't smile. It's not something to smile about."

"Yes."

How can I not smile when you're scolding me like this?

Qing went back to focusing on the treatment with a serious expression.

Honestly, treating external wounds was something that any experienced ronin could do, not just a doctor.

But the difference between having specialized knowledge and not was significant.

Unlike the ronin's treatment method, which would require reopening the wound later if it was just barely kept together, this was a high-quality medical treatment that would heal with just good medicine and care.

But, uh, I don't have any medicine……

For martial artists, there was the mystery of the universe, Qi.

If there was enough Qi, it could drive out most toxins and restore vitality, preventing wounds from festering.

But arrows had been lodged in her body for a long time, three of them at that.

She was burning with fever and her innate True Qi was depleting, not to mention her Inner Qi.

This was when elixirs were needed.

She had already taken a Great Rejuvenation Pill and left one for emergencies at the Divine Maiden Sect, so all she had…

Then, something came to mind.

But, is that really an elixir?

Qing took out her medicine pouch.

It was a keepsake left by the leader of the Green Forest, Wang Cheolgun, for Qing.

She had tried to determine what it was by taking a tiny bit and tasting it, but since it had been in the possession of a bandit leader, she was hesitant and suspicious, thinking, ‘Was this made by grinding up people or something?'.

But what else could she do?

The old woman was on the verge of death.

She had to save her first.

Qing scraped off a bit of the pill with her fingernail and licked it with her tongue.

Instantly, a cool and refreshing True Qi circulated, making her feel… Well, it's good medicine, isn't it? I guess even a bandit leader would want to carry around good medicine.

It's not like martial artists of the Demonic Cult only want to eat elixirs made by grinding people up.

If they were asked whether they wanted to eat a Human Flesh Pill or a Great Rejuvenation Pill, they would all choose the latter.

"Here, open wide."

"Is that an elixir? If you have something like that, you should give it to His Highn- Uub."

Qing shoved the elixir into Yan Pa's mouth as she was talking.

As she blocked her mouth with her palm, Yan Pa's tongue pushed against it, making it ticklish. Well, it's gross, just eat it.

"Zi Yu is a precious person, so he probably ate a lot of good stuff growing up. What's the point of eating more?"

"Uub."

"Also, you should lick your palm clean. Even a wealthy merchant who has everything in the world licks the lid clean, you know?"

"Uub."

"And an elixir is not as helpful as having a Supreme Master by your side. Just eat it and circulate your Qi."

Perhaps she thought there was some truth in that, as Yan Pa's resistance stopped.

Soon, she even managed to close her legs, which had been shot by arrows, and sat in a meditative position.

As expected, Inner Qi is invincible and Qi Treatment is god-like.

Watching Yan Pa, who had even closed her eyes and entered a state of meditation, Qing quietly slipped out.

As she blew on her hand, Zi Yu, who had been waiting outside, approached her and asked urgently.

"How is she? Is her condition any better? Is she going to be okay?"

"She'll probably recover if she rests for about half a year? Hmm, no, she's a Master of the Unrestrained Realm, so maybe three months? But she's old, so maybe half a year? Anyway, she just needs to rest well. But the problem is whether she can rest or not."

"Ahem."

"How did this happen?"

"We were on our way to the Prince's Manor in Nanning. Suddenly, arrows pierced through the carriage, and after that, I don't really know either. I was pushed and tossed around, and the world was spinning. When I came to, Yan Pa was lying beside me, dying."

"Who were the others? The, uh, Dog N?"

"Dog N."

I guess they're the same, but I can't call an elder Dog Old Man or whatever to his face, can I?

"We were traveling incognito, so our group was small."

"Still, you had Masters with you."

"They had sought refuge in the manor after being pushed out by the world. They have reasons why they can't move freely. Besides, even among them, I couldn't stop the most determined ones. But now, only Yan Pa is by my side."

Zi Yu's voice was filled with sorrow.

Even without looking, it was clear what kind of expression he had. 