\chapter{For Whom the Hammer Tolls (1)}

Naturally, any large city would have at least one street of metal shops.

After leaving the carriage at the inn, they asked for directions to the metal shops and headed back out to the streets.

Then there was something that felt missing.

"Come to think of it, no one came out to greet us?"

While she hadn't particularly expected it, the lack of the usual welcome made her feel empty.

When you don't know something, you just ask someone who does, and coincidentally, there was a muscle-bound weirdo in the group who answered even without being asked.

"There's no particular orthodox martial hall to speak of in Zhumadian, Sister."

"Oing? Why?"

"First of all, isn't it a city used as a major government stronghold? Orthodox martial halls are usually rare in cities where government influence is strong."

Clans (local gentry) cannot take root in government-controlled cities.

Rather, even halls that were originally established there end up being pushed out by pressure.

Moreover, orthodox martial halls are basically chivalrous people who don't listen to the government.

It was even more so after the Celestial Martial Emperor.

When the government borrows the power of Wulin, it's usually for dirty or unjust deeds they're ashamed of, so orthodox martial halls wouldn't respond to that.

However, unorthodox martial halls were bastards who actively approached government officials without even the pride (this is Zhuge Lixian's explanation) to refuse.

Moreover, since their usual deeds were dirty and unjust, they often took on government errands well.

So in cities tightly controlled by the government, orthodox factions dry up and only unorthodox ones swarm.

"Isn't that dangerous then? If it's swarming with unorthodox bastards."

"While the southeastern Zhongyuan, where the Unorthodox Path's influence is strong, certainly has that aspect, there's no unorthodox faction that would dare touch an orthodox martial artist in Henan."

Zhuge Lixian said with a gentle smile.

This was because the city's location was quite unfavorable.

To the north were Shaolin and the Beggar's Union, to the south was the Zhuge Clan, to the east was the Nan'gong Clan, and to the west was the Wudang Sect.

If the Unorthodox Faction acted up relying on government backing, they wouldn't be able to avoid annihilation from the combined forces of the Orthodox Faction from all directions.

"So at most, their mischief would be limited to ignoring us as if we don't exist, Sister."

"Hmm."

After arriving at the metal shop street like this, Tang Lan-Ah took the lead and guided the group.

Qing knew nothing about metal shop streets, and even Zhuge Lixian, who liked to talk, wasn't an expert in the field of needles.

However, Tang Lan-Ah wasn't a reliable guide either.

"Hey, you apprentice there. Who's the best needle craftsman in this city?"

Speaking informally right off the bat to a stranger was befitting of the Speaking Poison Flower's reputation as a villainess.

She only acted like a Chihuahua-level idiot when with Qing. Originally, she was a high-class young lady with no regard for others.

The poor apprentice was more distracted by her dazzling beauty than the sudden informal speech.

"Hey. What's this? Are you ignoring me?"

"No, no, I'm not. But what do you mean by needle craftsman? What craftsman in the world makes a living just making needles?"

"…?"

There are very few craftsmen in the world who specialize in needles.

Only in medical families like the Tang Clan, who also run metal shops, would they have a needle craftsman in the family to make them. As the apprentice said, how many needles could be sold to specialize in making them?

If there was a craftsman famous for needles, physicians from all over the world would come to buy them.

When asking for a needle craftsman at a local metal shop, the response would naturally be to ask if such a craftsman even exists.

"Then how do the physicians in this town make needles?"

"Well, if you just flatten it thin and long, it's a needle…"

Tang Lan-Ah frowned deeply.

Saying that flattening it thin and long makes it a needle was an outrageous statement that a physician absolutely couldn't let slide.

"What kind of stupid talk is that? Forget it. Then, who's the best craftsman in the city?"

"That would be Old Man Ban, but right now he's…"

The apprentice tried to say something, but Tang Lan-Ah, who had already lost her patience, immediately barked at him.

"You talk too much. Which way do I go?"

"Go straight and at the second alley…"

The apprentice explained the way.

Unexpectedly, the metal shop street seemed quite developed, as the directions were quite complex.

Surprisingly, Tang Lan-Ah nodded and said with an expression of complete understanding.

"Little Brother Zhuge? Did you remember?"

"Of course, Sister Tang."

"Then let's go."

Qing nodded at this scene and thought.

\textit{People should naturally leave things they can't do to others.}

\textit{Even if she seems like a quack, she's still a physician, so it seems she's not completely incapable of using her head.}

Zhuge Lixian, fully demonstrating his status as the top intellect among muscle men, showed the marvel of memorizing the complex directions heard just once and leading the group.

Finally, arriving in front of the Ban Family Metal Shop, said to be the best in the city, Qing asked.

"Hmm. Zhugie, is this the right place?"

It was a building that didn't seem to have been used for a long time.

In the open space characteristic of metal shops with just a roof, fresh weeds had already grown up to ankle height.

Considering it was early spring before even cherry blossoms had bloomed, it meant it hadn't been managed at all.

"Sister, we've come to the right place. Look, it's right there. Ban Family Metal Shop."

Zhuge Lixian pointed to a signboard lying on the ground.

The signboard, made of iron plate befitting a metal shop, clearly had the four characters for "Ban Family Metal Shop" engraved in elegant calligraphy.

"Just looking at the signboard, it's clear this is a craftsman of extraordinary skill. However…"

Even if he was a layman when it came to needles, the Zhuge Clan's metal shop was also one of the famous names known throughout the world for its precise mechanism production.

The level of craftsmanship could be seen just from the characters engraved on the signboard.

"Well, we'll know when we go in. Hello? Is anyone here?"

Qing said this as she darted into the metal shop that looked almost like an abandoned house.

"What's this, did the shop go out of business?"

And as she looked around inside, suddenly—

Her eyes met squarely with those of an old man quietly glaring from the shadows.

"Aaack! Shit, you scared me…"

Qing let out an unladylike, strong scream.

But that was only for a moment.

The only things she feared were ghosts or a sudden nuclear noogie from her master falling from the sky, not just an old man glaring.

"Excuse me, grandpa? Are you okay? Why are you like this? You scared me."

"Now you're even mobilizing women! Get out! Even if I die, I have no intention of forging weapons for you bastards!"

The old man shouted vehemently.

"Oing? We came to make needles, not weapons."

"Ha! Aren't hidden weapons still weapons?"

"No, not those needles, but long needles. The ones physicians use for acupuncture. Don't you know needles? Needles? Has grandpa already gone senile?"

At this, the old man's expression turned to bewilderment.

"You came to make needles? Not to ask me to make swords?"

"I already have a sword, you know? Why would I use another sword when I have the one my master gave me?"

Qing said, tapping her scabbard.

Only then did the old man show an embarrassed expression.

"Ahem. Yes, you came to make needles… It's been a while since I had customers… Needles are quite expensive, though."

"Ah. Wait a moment. I'm not the one buying them."

At this, Tang Lan-Ah held out the broken needle.

As soon as Blacksmith Ban saw the broken needle, he let out a deep sigh.

"Oh my, how did you break such a precious needle? Just looking at it, it's undoubtedly a divine relic that might appear once in an era."

"Could it possibly be reattached?"

At this, the old man carefully examined the broken cross-section.

"Tsk tsk. How much force must have been used for this excellent needle to break like this? As they say, ‘pearls before swine,' it seems the tool is a divine item of the world, but the owner's skill falls far short."

"What? What did this old man just say?"

"Still, fortunately, the cross-section is clean, so it shouldn't be difficult to reattach."

Tang Lan-Ah's face turned bright red.

"What does an old man know? What kind of muscle blocks a needle wrapped in Inner Qi? It would be easier to stick a needle in a rock."

"Ah. So the young lady was doing acupuncture. This old man has made a foolish mistake."

"Hmph."

Tang Lan-Ah snorted.

"So, where's the other half?"

"Uh. About that."

Tang Lan-Ah looked at Qing.

"Speaking of which. Old man, don't you have those thin tongs used for making needles? We need to pull out something stuck in a body…"

The broken needle was stuck in Qing's shoulder with just the tip slightly protruding, so it was in a state where it couldn't be pulled out without a proper tool to grip it firmly.

It was too short to grab with hands as the protruding part was only as big as a millet grain, and fingernails would slip on the metal and couldn't apply enough force to pull it out.

Moreover, ordinary tongs couldn't even grip the thin long needle tightly.

Fortunately, among the tools the old man had collected over a lifetime of running a metal shop, there was a pair of tongs for gripping iron needles.

"Alright, shall we pull it out?"

"If you pull it out and it's broken in half, I really won't let it slide. I'll shout as my Hidden Dragon Tournament victory speech that the Tang Clan's Whatever Lan-Ah is a quack physician who kills patients."

"Ugh."

Suddenly, Tang Lan-Ah's movements became stiff.

Qing narrowed her eyes.

"What's this, surely there's no real possibility of that, right?"

"It's all because of you, Qing'er! Your muscles are compressed like rocks, not even like Ten Thousand Year Cold Iron, so if the needle can't withstand it and twists…"

"Yes, it's my fault, my fault, all my fault."

"Well. Anyway. Ah, over there!"

"Huh? What? What's there-"

Swoosh, there was a clear feeling of something being pulled out.

A sigh of relief followed.

"Phew, it came out safely and well."

"To induce carelessness, what a vile trick…"

"Come on. How can you say such things even when I speak?"

Tang Lan-Ah laughed and slapped Qing's back.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And then Old Man Ban was in a fuss about having to light the fire again.

Anyway, it wasn't particularly interesting for Qing, who didn't know anything about metal shop work, to watch.

"Come to think of it, Old Man Ban. Are you perhaps a descendant of Ban Chi?"

"Ah, Sister! You know Ban Chi! He was truly the greatest blacksmith of all time!"

"Uh, yeah…"

It was the usual nonsense Qing spouted.

Hearing it from someone else's mouth made her feel strange.

\textit{Isn't this guy like actually from Zhongyuan?}

\textit{Is this the true spirit of pretending to know things? One that transcends time and space itself?}

"Actually, metal shop work is hard and tiring, and doesn't bring in much income, so usually children inherit it. In fact, unless you're skilled enough as a craftsman to amass some wealth, even getting married isn't easy…"

So often, they pick up orphans, raise them, and pass on their skills.

Of course, in most cases, they substitute wages with the cost of skill transfer, so they're usually no different from servants cum assistants who are just provided with room and board.

Some craftsmen with personality issues even work them like slaves until their bodies break down and then kick them out.

"That's why many blacksmiths have the surname Ban. It means they want to emulate the greatest craftsman among craftsmen."

"Hmm."

"Ah. Speaking of Ban Chi, I can't help but mention his beautiful love story and the Fushen-di. The Fushen-di refers to Ban Chi's treasure that has now disappeared forever, a flute made of Ten Thousand Year Cold Iron…"

Qing stretched out her hand to the side.

Then Jian Buxi took out a flute from somewhere and placed it firmly in that hand.

It was thanks to Cui Liweng having completed the handover.

"Zhugie. This is that Fushen-di that was said to have disappeared forever."

"…It really is Ten Thousand Year Cold Iron. Is it genuine?"

The Zhuge Clan's metal shop is famous.

And Zhuge Lixian was knowledgeable about all the business his family was involved in.

He could recognize at a glance the characteristic lusterless dark blue appearance of Ten Thousand Year Cold Iron.

"Then what? Would it be fake?"

"My goodness, such a treasure…"

Qing succeeded in temporarily sealing the never-resting terror of a chatterbox by placing the Fushen-di in Zhuge Lixian's hand.

However, the peace for her ears that had come after a long time did not last long.

"What's this, old man? Who said you could light a fire?"

"Didn't we tell you to close up shop?"

"Who's there? What fearless bastards dare to violate the laws of the Namen Sect…"

It was thanks to a group of thugs who appeared wearing swords loosely.

Qing smiled brightly as she confirmed their Evil Karma.

\vfill
\begin{lstlisting}
The chapter title is a reference of the phrase 'for whom the bell tolls, it tolls for thee' from John Donne's prose 'Devotions Upon Emergent Occasions, and severall steps in my Sicknes'.
\end{lstlisting}