\chapter{For Whom the Hammer Tolls (2)}

Qing waved her face veil side to side as she greeted the guests.

"Well, well. Aren't these our friends?"

"…?"

"Yes, what brings you all the way here? What business do you have at this crumbling metal shop?"

The thugs hesitated.

'What's this? Does she know us? Why is she acting friendly?'

'Is she one of us? Perhaps she's from the Unorthodox Path?'

"Um, who might you be…"

"Would you know who I am if I told you? Come on. So. Why are you here? I haven't been in this neighborhood long, so I don't know what's going on."

In fact, thugs also have a sort of script prepared for when the other party takes a strong stance.

If Qing had shouted something like 'You scum, what are you doing to innocent civilians!' as an orthodox martial artist might, the thugs would have had a manual for how to respond.
'We are the virtuous experts of the Namen Sect!'

'If you mess with us, the Namen Sect won't stand idle, and if the Namen Sect doesn't stand idle, all the unorthodox factions in the city won't stand idle, and if all the unorthodox factions in the city don't stand idle, the government officials who took our bribes won't stand idle either!'

They were prepared to recite something like this in a rough tone mixed with curses.

But to confidently act friendly?

This was often the attitude shown by infamous Demonic Adepts to cute unorthodox faction saplings.

Of course, Demonic Adepts don't act friendly because they find the juniors cute.

Usually, it's to exploit them.

This was how the seniors and juniors of the Unorthodox Faction typically behaved.

That's why the thugs became even more tense.

"Well, we are martial artists of the Namen Sect, but."

"Namen Sect? Ramen Sect? Little Brother, can you explain?"

"The Namen Sect, a group that flourished about ten years ago, I heard their leader is a leper. I believe I heard his realm is Transcendent."

"Ah. That Namen Sect? Ah, I want to eat ramen."

Zhuge Lixian scratched his chin.

No matter how he thought about it, he had never heard of a dish called ramen.

But originally, Zhongyuan were so vast that if one were to count local dishes, one couldn't name them all even if they spoke of them from birth to death.

And Zhuge Lixian didn't hold back when he was curious.

To be precise, he couldn't hold back when he was curious.

"Sister, I haven't heard of a dish called ramen, but which region's food is it?"

"Hmm. I heard they call it lamian around here."

"Ah, a dialect. I understand."

The Namen Sect martial artists froze even more upon seeing Zhuge Lixian.

Originally, the less skilled a martial artist was, the more they cared about the other party's level of External Arts.

Of course, since the criteria for judging External Arts for low-class martial artists without discernment was size and muscle, a huge muscle man was already no different from a Supreme Master.

And to be the Sister of such a Supreme Master!

"So. What's the matter?"

"Well, that old man dared to defy the Namen Sect's orders, so we came to teach him a lesson…"

"Teach him a lesson? Can you explain in more detail?"

The Namen Sect martial artists, overwhelmed by Zhuge Lixian, obediently revealed their purpose.

There was also a reason why Qing had acted in a somewhat friendly manner.

Old Man Ban is the best craftsman in Zhumadian.

In fact, it's a bit ambiguous to say he's the best in Zhumadian, as he was one of the top master craftsmen even if you expanded the range to the entire Henan Province.

However, the master craftsman's specialty was limited to agricultural tools and the like.

No matter how excellent an ironsmith is, they can't make masterpieces if the field is different.

If a master of swordsmanship picks up a half-sword, they might be able to swing it roughly, but they couldn't be called a master of the half-sword, could they?

The problem was that a sword Old Man Ban made in his youth had been discovered.

And it was said to be a truly excellent sword.

In other words, Old Man Ban wasn't unable to make swords, he was unwilling to make them!

Skilled sword craftsmen are precious people that sects compete to recruit.

If martial artists are perfectly equal in skill, the difference that determines victory or defeat would be the superiority of their weapons.

Even if not, martial artists' interest in better weapons was something that even masters of Fist Arts couldn't hide.

And the excellent sword craftsman of Zhumadian should rightfully be taken by the Namen Sect, the Unorthodox Faction leaders of the city.

"So you want to take Old Man Ban away?"

"No, we gave up on that long ago. That old man is so stubborn…"

Old Man Ban had sworn not to make weapons.

Craftsmen who have the ability but refuse to make weapons are more common in Zhongyuan than one might think.

If you throw a silver coin to a street storyteller, you could listen to tragic stories about this all day.

No matter how they coaxed, threatened, and tried every method, Old Man Ban remained unmoved, insisting he'd rather die than make swords.

Even kidnapping and threatening his grandson didn't work.

So the Namen Sect leader thought.

'If I can't have him, I'll destroy him.'

'How can I make an example?'

'Right, let's starve him to death.'

'If they see a bastard who dared to defy the Namen Sect die of starvation, others won't dare to think differently.'

"Ah. So that's why you come to chase away customers every time?"

"Yes, well, that's how it turned out…"

The Namen Sect martial artists answered, looking anxious and trying to gauge the situation.

However, they became more relaxed at Qing's next words.

"Wow, that must be tough. Really tough. So you've been watching the metal shop all day, checking if he lights a fire or not?"

"That's right. We all take turns watching to see if anyone gives the old man food. But some bastard keeps sneaking in food, so the old man won't die. And the higher-ups keep pressuring us, asking if we're not blocking properly…"

This was the life of a low-ranking martial artist.

Especially for Unorthodox Faction members, how much worse must it be?

"Life seems tough. Want me to help?"

"If, if you're offering to speak to the higher-ups for us, we're fine, you really don't need to…"

"No. We need to remove the fundamental cause."

"Pardon?"

"Life is hard? Then just don't live. A life that only chooses to do bad things, what's the point of living more?"

"…?"

Qing stretched out her left hand.

However, feeling nothing in her hand, she frowned and looked at Zhuge Lixian.

"Zhugie, when I do this, you should know what to do! You should put the Fushen-di in my hand! Didn't you see what Sworn Sister did earlier?"

"Ah, I'm sorry, Sister. My apologies."

Qing grasped the Fushen-di in her hand.

Then, barbaric Qi output burst forth from the Ten Thousand Year Cold Iron short staff.

Somehow, Tang Lan-Ah had taken up position at the rear, blocking the metal shop entrance with a poison bottle in hand, and Jian Buxi was beside her, cutely raising her fist with three fingers extended to shoulder height.

The Namen Sect martial artists, blocked front and back, spoke politely with pale faces.

"Uh, if you have any grievances, perhaps we could resolve this through dialogue?"

"What dialogue with Unorthodox Faction vermin? I'm from the Divine Maiden Sect. This is a Zhuge. That nasty face over there is from the Tang Clan. And next to her is… um… Xue Clan Trading Company?"

At this, Jian Buxi made a tearful face.

But it's not like she could say Bliss Palace or Demonic Cult, could she?

Qing thought for a moment and changed her words.

"Cancel that about the Xue Clan Trading Company. She's my Sworn Sister."

Jian Buxi's expression brightened again.

She seemed satisfied.

On the other hand, the Namen Sect martial artists were not satisfied.

Except for the Xue Clan Trading Company, these were names known to all Wulin practitioners under the heavens.

"Damn it! Attack!"

Even among low-ranking members, there's a hierarchy, so the highest among them shouted.

At the same time, he immediately jumped to the side.

One followed the order and rushed at Qing, while another jumped back and tried to break through to the entrance.

Qing calmly looked at the Namen Sect martial artist rushing towards her.

Raising his sword high above his head as he charged, it didn't matter whether he was a Wulin practitioner or a samurai; either way, his torso was wide open.

It was a gap at the level of politely asking, 'Please stab my torso'.

So Qing simply extended Fushen-di forward.

The short staff, imbued with barbaric strength, entered the upper abdomen and angled upwards, reaching the heart in one go.

"Ugh."

The vicious Unorthodox Faction bastard couldn't even bring down the sword he had raised above his head, dropping it with a Clang.

"Uh, uh…"

In Zhongyuan, there's a weapon called a Blood Hammer, which is a hollow awl with a hole.

If you stab the heart with this, blood enters through the hole and gushes out, creating a spectacular scene.

This was what was happening in Qing's hand right now.

Blood spurted out regularly from each air hole of the Fushen-di, matching the heartbeat.

The stickiness wetting her hand was something she hadn't felt in a long time.

The blood touching her hand, always cold due to Demonic Arts, felt so hot it might burn.

Qing couldn't control her expression, her mouth corners pulled up to her ears in a vicious smile.

It was fortunate she was wearing a face veil.

Zhuge Lixian frowned at this sight.

"Ugh, Sister. Isn't it unpleasant to have blood enter the flute?"

"It's fine if you wash it well. What. Should a martial artist be picky about weapons?"

"Even if you try to gloss over it with such cool words, the Fushen-di wasn't originally a weapon. But!"

Zhuge Lixian suddenly spat out his words.

"As expected, your flowery and bewitching eloquence is still the same! To make the enemy spill information without any kind of torture or coercion! This dull brother is moved! Moved again! I was starting to suspect recently that you might just be a stupid woman, but you shatter my foolish thoughts completely!"

"What's this? Why do I feel like shit even though it seems like I'm being praised?"

Anyway, Qing was very satisfied after getting a proper taste of this feeling in her hand after a long time.

Piercing through soft skin and tough heart muscle, she got to taste both weak and rough sensations simultaneously.

And stabbing with the Fushen-di made blood gush out, \textit{Oh, it's a complete rediscovery of the flute}.

It was a discovery that would make Ban Chi weep tears of blood in the afterlife.

The group's level of force was too excessive for dealing with mere neighborhood Unorthodox Faction dregs.

The one who ran for the door had his head pierced by Jian Buxi's finger-pointing, with some contents leaking out.

The one who tried to escape alone was in a slightly better state, with Tang Lan-Ah's whip wrapped around his neck, his eyes rolled back and foaming at the mouth.

"Why did that one faint?"

"Fire ant poison entered his arteries. He probably felt like his whole body was on fire."

"Hmm."

On second thought, he might be the most pitiful.

That's when it happened.

"You damned baSTARDDDDDD!"

Old Man Ban suddenly charged with bloodshot eyes, raising a huge hammer high above his head in the familiar posture Qing had just seen.

In that direction lay the martial artist foaming at the mouth, with the whip wrapped around his neck like a scarf.

Qing gracefully flew with the ultimate form of the Divine Maiden Footwork, Spatial Leap, to block in front of the old man.

"Wait, grandpa."

"Get out of the way, I'm going to smash that bastard's skull to pieces! That damn bastard!"

"I understand how you feel, but for someone who said they won't make swords, is it okay to kill people with a hammer?"

"But that bastard, that bastard…!"

"Ah. It can't be helped. Be satisfied with this."

Qing placed the sole of her shoe on top of the fallen Unorthodox Faction martial artist's head.

Her knee trembled for a moment as she applied force, and finally, Crunch.

In fact, from the moment Qing said it couldn't be helped, her expression behind the face veil was already blooming with a wide smile.

Qing staggered for a moment as if she had lost her balance.

To her companions, it looked as if she had been shocked by the sensation.

Of course, she was shocked.

\textit{Wow… This is really amazing. How long has it been?}

\textit{Hmm, it must have been too stimulating after such a long time.}

\textit{I wonder how many spare underwear I packed.}

Cui Liweng's foresight in preparing the face veil was shining brilliantly, emitting a dazzling radiance like the sun.

But good things are good things, and having sticky shoe soles is doubly unpleasant.

Qing dragged the soles of her shoes across a clean part of the floor.

Old Man Ban, who had witnessed the Namen Sect martial artist's miserable death, stared blankly at the corpse instead of reflecting.

Then he hacked up phlegm and spat it out with a Ptui between the broken remains.

Seeing this, Qing spoke up again.

"Grandpa, don't we have something to talk about too?"

At this, Old Man Ban subtly averted his gaze.

Qing took a crooked stance and continued her questioning.

"You said this wasn't a matter of just a day or two, right? You must have known these guys would rush in if you lit a fire."
