\chapter{For Whom the Hammer Tolls (6)}

The bandaged man quickly examined the Disciplinary Officer.

Qing was quite tall, and a martial artist who had undergone Overhaul Rebirth naturally had long limbs.

When Qing raised her hand holding the wrist to its full extent, the old man's corpse floated about half a chi in the air, swaying.

It was a hair-raising scene with a double whammy.

First, it was chilling to see a formidable opponent who had subdued a Late Stage Transcendent Realm master right before their eyes, and second, thinking of the consequences of the Unorthodox Path's Disciplinary Officer's death sent shivers down their spines.

It was truly a case of adding insult to injury.

"I am Duan Yunxiao\footnote{段運削. Dan Unsak (단운삭) in the original text}, the Namen Sect Leader. Who on earth are you to commit such an outrageous act?"

Duan Yunxiao tried to speak without his voice trembling, but a slight vibrato like a singing technique mixed in.

"Is there a need to reveal names when cleaning up trash? It's just those who are bothered doing the cleaning."

"Hmm…"

Duan Yunxiao let out a heavy groan.

Translating their conversation into Wulin-speak, it went like this:

‘Let's talk this out.'

‘Shut up and come at me.'

As a five-year veteran of Wulin, Qing could now not only interpret but also speak the language of Wulin quite excellently.

And she didn't stop there; she could even apply it.

"However, the possibility of saving your life isn't entirely gone. Hand over Old Man Ban's grandson."

Beside her, Zhuge Lixian inwardly admired.

\textit{As expected, Sister! You don't say you'll back off even if they hand him over!}

\textit{Since you said ‘possibility,' isn't this a scam-like trick where you can say it was just a possibility if it doesn't work out!}

By now, Zhuge Lixian had come to understand about eight-tenths of Qing's character.

Once she decided to mess someone up, she was a persistent and vile expert who wouldn't hesitate to use any means - be it words, swords, poison, or fire - until she was at a disadvantage.

While she had no concept of face, she somehow seemed righteous, so it was a perfectly fitting description.

"Kuk. You may call us trash, but aren't you also after Old Man Ban in the end!"

"Rescuing a grandson is much better for appearances and bragging than kidnapping one. How can you compare? Is a feast just prepared the same as food that's been rotting for half a month? Do you think all food is the same just because it's edible?"

"No matter how you dress it up, in the end, it's still the same ugly greed to possess the greatest sword craftsman under the heav-"

"Enough. Hand over Old Man Ban's grandson. Weak bastards can't just say ‘Here you go' when told to hand something over. Why is your tongue so long?"

"That's…"

At that moment, Zhuge Lixian leaned close to what he presumed was Qing's ear under the face veil and whispered.

"Sister, I don't think they can hand over Old Man Ban's grandson. The inspector mentioned evil decoctions, so probably…"

The rumor that lepers eat children was originally just a false accusation born from prejudice.

However, rumors are the world's most vicious things.

They shake the hearts of the desperate, making them believe it's the truth.

And leprosy, where flesh rots and falls off while still alive, was such a horrific disease that it was called the Judgement of Heaven (Heavenly Punishment).

Qing's eyes lost their luster, cooling to an inorganic texture.

A faint purple light leaked from the eye holes behind the face veil.

It was the light of a malevolent star that people instinctively avoid, realizing as soon as they see it that it is something very harmful and terrible.

"I should have just set fire to everything earlier."

"I agree."

Qing dropped the old Great Demonic Adept's corpse with a thud and gripped the Moonlight Sword with her right hand.

While it wasn't so bad that she couldn't use her left hand, still, it felt more familiar and fit perfectly in her hand when holding the sword in her right hand.

"Seeing your covered face, you must be the Namen Sect Leader? People in Jianghu say there's not a single normal face among those who cover their faces."

Everyone present looked at Qing with strange eyes, but…

As Qing was a proud beauty, she had nothing to be ashamed of.

"I should let the world know how ugly you are by hanging you up high to dry. You eat people because you have nothing to eat? You dog-like-"

"Wait! It's a misunderstanding! There's a misunderstanding!"

Duan Yunxiao shouted urgently.

Qing tilted her head crookedly.

"Misunderstanding? What misunderstanding?"

"The horrible rumors about decoctions and such are not true! Who would believe such rumors!"

"Not rumors? Clearly, that dead security deputy-"

"Sister, it's Disciplinary Officer. But security deputy, was it… Why does that sound so cool? Somehow it makes my heart feel warm-"

"Enough. That Disciplinary Elder said you were making medicinal decoctions."

At this, Duan Yunxiao spoke with an aggrieved voice.

It was truly an aggrieved voice.

"We sold Old Man Ban's grandson to the black market long ago, we gave up on such ineffective superstitious prescriptions a long time ago!"

"So you did try eating them? No need for further questions, then!"

Qing stomped on the ground and shot out like an arrow.

Sword Threads, now forming the shape of a huge single blade, completely covered the Moonlight Sword, leaving a thick twilight-colored trajectory.

"Ha, damn it! What are you doing! Attack!"

Duan Yunxiao shouted as he drew his sword.

A faint starlight shimmered on the blade; by the Late Stage Transcendent Realm, one is skilled with Sword Force even if it's not fully compressed.

Sword Qi and Sword Force cannot be compared.

However, it wasn't easy to break through Qing's barbaric output with the less compressed Sword Force of a Transcendent Realm Master.

Qing continued her sword strikes, riding the momentum.

Fūrinkazan; when it strikes, it's like a storm.

The latter moves of the One Hundred And Eight Asura Sword, Eleven Thousand Strikes, a swift sword relying on wildness with countless afterimages, struck mercilessly up and down, left and right without discrimination.

As Duan Yunxiao kept retreating and deflecting the sword strikes, he thought to himself.

\textit{Why does this seem manageable?}

\textit{Although the purple light in her eyes trailing like a tail was terribly eerie, and the Sword Threads extending in one mass were bizarre and unheard of-}

Nevertheless, since she wasn't using Sword Force, this was what it looked like when a Peak Realm Master crudely increased only their Inner Qi.

"Damn it! I've been fooled! This bitch isn't a Master!"

"What are you saying? You see this body? Master."

"What are you all doing! Why aren't you rushing in!"

Duan Yunxiao shouted, but his disciples instead retreated and hesitated.

To the low-class without discernment, Qing's vicious Sword Threads seemed a hundred times more dangerous than their leader's faint Sword Force.

The First-Rate and few Peak Realm martial artists with discernment were watching Qing's companions keeping their distance behind her.

Anyway, since the Blood-Forged Sword Demon had died, they were certain there must be a Master among them or some technique equivalent to one.

So they thought it better to watch the duel and rush in to quickly turn the tide if their leader gained the upper hand, or surrender if he was defeated.

From the beginning, the one thing that unorthodox sects consistently emphasized most was the loyalty of virtuous experts, believing in such qualities.

Because they were people without loyalty, they emphasized and re-emphasized it until their ears were calloused.

"You damn bastards!"

Duan Yunxiao ground his teeth.

In the end, he had to do it himself.

No matter how vast her Inner Qi, could he really not defeat a mere Peak Realm girl?

Duan Yunxiao deliberately put on a troubled expression and started acting as if he was being pushed back, retreating one step at a time.

Then, in the gap between sword and sword, his eyes flashed, and he dove in with a sharp sword path through the opening in Qing's arms.

It was one of the few excellent moves in Duan Yunxiao's life, a strike containing the essence of a counterattack.

In the momentarily accelerated thought process, in a world slowed down just as much, the girl raises her arm to block the sword's trajectory.

In the slowly flowing world, Duan Yunxiao's mouth slowly draws a long arc.

\textit{You stupid bitch, do you think human flesh can block Sword Force?}

Finally, Duan Yunxiao's Sword Force touches Qing's forearm, raised diagonally.

In time that now seems almost stopped, the Sword Force seeping into the white skin is visible.

At the moment when Duan Yunxiao believed without a doubt that that beautiful forearm would be cleanly cut off-

An intense impact hit his hand!

It was like striking an iron block, making his skin scream and sending a stinging pain through every joint as the shock traveled.

"How…"

Right on cue, Qing's right arm that had left its place returns.

Realizing there's no way to avoid the slashing strike coming for his waist, Duan Yunxiao completely takes the strength out of his legs and falls backward.

Qing's sword blade barely grazes the tip of Duan Yunxiao's nose, drawing a crescent.

Duan Yunxiao accepts the impact on his back with relief and immediately flips his body over vigorously.

Lazy Donkey Roll. It's a type of Qinggong meaning "lazy donkey turning over," which is simply a technique of rolling on the ground.

Wulin practitioners who value face as much as life unanimously say they'd rather die than roll on the ground so unsightly, but when the critical moment comes, no one chooses death over face by not rolling.

And yet, they go on about Han Xin and crawling between legs.

It was Han Xin's great mistake to provide an excuse that would be milked for over a thousand years.

Qing stomped her foot.

The rough pressure of the Heavenly Demon Reigning Step firmly presses down on the surroundings.

The advantage of the Heavenly Demon Reigning Step is that since the energy gathers in the soles of the feet, you don't have to see that disgusting Qi full of eyes.

It meant she could use it roughly without worrying about appearances.

Duan Yunxiao, who couldn't even roll a few times, groaned at the suddenly doubled pressure.

Following that, with the Deng sound of the Buddha's Palm, blood spurted from the thigh of the lying man with a swoosh.

"Argh!"

Duan Yunxiao grabbed his thigh and screamed for his life.

The inside of the thigh is unexpectedly one of the most critical weak points.

It's a passage where one of the thickest blood vessels passes unprotected without muscle protection, so uncontrollable massive bleeding occurred below Duan Yunxiao's pelvis as his femoral artery burst.

Still, being somewhat of a Master, he dug into the wound and tightly gripped the blood vessel with his fingers; though not a technique of the True Fire of Samadhi, a couple of streams of white smoke along with a savory smell permeated.

He stopped the bleeding, but he lost one leg.

Even a Peak Realm martial artist other than Ximen Qing could sufficiently handle a one-legged Transcendent Realm master.

Qing grinned as she looked down at Duan Yunxiao.

"The crime of not recognizing a Master? The death penalty."

In fact, it was a ridiculous statement.

There was a difference when it came to enlightenment of the sword from the start, so even amidst the chaotic flurry of strikes, hadn't Duan Yunxiao found an opening and launched a fatal counterattack?

If it weren't for the White Hand Demonic Arts' Vajra Invulnerability, no, since it was at Peak Realm level it was a bit weaker, so maybe it could be called Gold-Plated Invulnerability or Silver Invulnerability White Hand. At any rate, without that, her forearm along with her torso would have been neatly cut.

If it weren't for the Heavenly Demon Reigning Step, he would have jumped up and rushed in again, and without the Buddha's Palm, how could she have struck the air and burst his thigh?

However, it was also a very natural tactic for martial artists to hide one or two secret techniques.

Qing was just hiding a bit more than others.

In professional terms, if you don't know, you have to fuck around and find out.

It was a precious truth that has been passed down from the emergence of humanity until now.

And when victory and defeat were decided, there was also something the loser had to do, established since ancient times.

"Pl-please spare me. Whatever you want, I'll give you everything, so…"

"I already told you what I want. Old Man Ban's grandson. Can you bring him right now?"

"Time, please give me time. Since we sold him to the black market, if we inquire around, we can surely find him…"

"Hmm. An opening! This is for my arm!"

Qing scratched her chin and naturally lowered her hand, then suddenly extended her arm, Deng!

Pak! With blood spurting, Duan Yunxiao's arm below the elbow fell off and rolled on the ground along with his sword.

"Argh! Why! Why!"

"The way you were moving your eyes was suspicious. Your posture was off from the start. If you want to live, you should know how to rub your hands together like a fly, why are you gripping your sword tightly with your hand turning white from the force?"

There's actually a technique called Sword Breaking.

It's a technique where you violently infuse True Qi into the sword blade to shatter it, and if done clumsily, you'd just ruin one weapon and that's it.

However, a properly refined Sword Breaking technique is truly like the Great Generals' Cannon, with over a thousand sharp fragments filled with True Qi being fired.

Qing just thought it was suspicious, but it was actually the final technique Duan Yunxiao had been secretly preparing.

Originally, Qing's fights were all about intuition and cunning, so she was extremely sensitive in these aspects. As such, it was inevitable she would notice.
