\chapter{For Whom the Hammer Tolls (4)}

The main gate guards are usually one on each side, so the remaining one shouted angrily.

"What are you doing! Even after this…"

"Do you want to fly too? Or will you run on foot to deliver the message? Tell them to hand over Old Man Ban's son."

Qing cut off the guard's words.

Zhuge Lixian added to Qing's words.

"It's his grandson, Sister."

"Damn, why do I keep saying son? Anyway, you can clearly see I'm stronger than you, right? Want to die gloriously by resisting?"

"Keuk, you bitch won't die peacefully. Hup."

The Namen Sect martial artist was trying to curse out of pride, but as something touched his Adam's apple in an instant, he immediately shut his mouth.

"Want to say bad words? You should show respect to Masters."

If they show any sign of fighting, she switches to no-words mode.

At these times, Qing's words come from her spine, skipping the process of going through her head.

However, it's the way of the world that the weak follow whatever the strong say.

"No, no. I must have lost my mind for a moment."

"Good. Go and tell them to bring Old Man Ban's grandson from the metal shop. While you're at it, take that friend who failed at flying too."

"If, if you could please remove this first…"

Qing obediently removed Fushen-di.

The Namen Sect martial artist cautiously picked up his comrade and fled inside the main gate.

And just as they seemed to have gained some distance.

"You damn bitch! Did you think you could touch the great Namen Sect and live?! How ugly must you be to cover your face with…"

"Lan-Ah. Isn't it a bit noisy?"

"…I'll tear your crotch apart and kill you, you bitch! I'll right now- Ack!"

Suddenly, the Namen Sect martial artist who shouted what sounded like a slogan from a certain amphibious assault unit grabbed between his legs.

\textit{Ow.}

Qing frowned and looked at Tang Lan-Ah.

With a reproachful look that said, 'No matter how dirty his words were, isn't that going too far?'

For reference, Qing had a nickname given by the soldiers of the Chengdu Garrison in Sichuan, namely the Absolute Witch, the Demonic Maiden Who Ends Bloodlines.

"He was saying dirty things, so I just…"

This is why people should be careful with their words.

Trying to tear someone else's crotch, didn't his own crotch get torn instead?

"What's this! What's going on! We're under attack! Ring the bell!"

A courtyard behind the main gate is common sense in both the East and West.

Witnessing their comrade becoming a eunuch in the middle of that courtyard, the startled martial artists ran around in confusion, grabbing their weapons.

Ding ding dong ding!

The loud sound of striking metal was chaotic.

Originally, the signal to alert of a surprise attack is designed to grate on people's nerves to the point of being unbearable.

"Lan-Ah, you're making us fight because of you. If you had let them deliver the message quietly, we could have left quietly with Old Man Ban's grandson."

"Huh? I just… because he was cursing at you…"

"Alright, get ready. Zhugie and Sworn Sister, beat up anyone rushing out of the main gate and be ready to run at any time. Lan-Ah, stay behind me- no, if you stick that close, how can I fight?"

"Ah. Sorry."

It was a cute mistake due to lack of real combat experience.

Qing blocked the main gate and drew out the Moonlight Sword (No. 8) instead of Fushen-di.

Although there was a big tooth missing in the middle of the blade, it didn't matter as long as the core wasn't damaged.

As Qing faced the enemies rushing in like that, she thought she looked like Zhang Fei blocking the Changban Slope… or was it the Battle of Changban?

\textit{Hmm, was that the right name? Changban? Was that it?}

\textit{Wasn't it blocking a bridge? Changban Bridge? Ban Bridge?}

The sight of them rushing out in chaos was like an anthill that had water poured on it.

The Namen Sect martial artists formed a semicircle around the main gate.

Among them, a middle-aged man with an ominous aura stepped forward and shouted.

"Where are you from to be so rude!"

"Your evil deeds end here! Hand over the grandson of Craftsman Ban from the metal shop that you kidnapped!!"

Qing glanced behind her.

With the chaotic sound like striking a pot, spectators had gathered all around outside the Namen Sect.

Seeing this, the middle-aged man seemed to have guessed the situation outside the main gate.

"Ahem, do you dare to accuse the great Namen Sect of such an outrageous crime? Although we belong to the Unorthodox Path, we are righteous experts who proudly uphold the law of the land."

Qing grinned.

He was someone who didn't even know the basics when it came to a warfare of public opinion.

After all, one should emphasize important words loudly so everyone can hear.

"You even have the audacity to lie!! Clearly, Old Man Ban from the metal shop knelt down!! Crying!! And pleaded that you bastards kidnapped his grandson!! And threatened him to make weapons!! Didn't you!"

At this, the middle-aged man smiled slyly.

"That's strange. But there are so many who try to slander our sect, even if you shout like that, everyone is used to it. Wouldn't it be better to speak nicely instead of straining your voice?"

After all, the spectators know everything.

It was mockery, saying did she think they would charge in with brooms or something if she tried to incite them?

A vein slightly popped up in the corner of Qing's forehead.

\textit{Is this shameless bastard pulling a 'So what are you going to do about it?'?}

Qing's brain, which only worked when screwing others over, started spinning rapidly.

\textit{Should I go with Operation Cooking Master Boy?}

\textit{Actually, I could sell out my master saying I'm a special disciple, and since we're in the middle of a group project, sell out the Zhuge Clan, sell out the Sichuan Tang Clan, but hide the Demonic Cult because that's a bit much, then they'd immediately turn serious and bow subserviently…}

\textit{But that wouldn't be any fun.}

\textit{For a neighborhood unorthodox faction, they had quite a high Evil Karma count, which was very suspicious.}

Qing called Tang Lan-Ah in a small voice.

"Hey. Lan-Ah."

"Hm?"

"That poison bomb, is it strong? Can't you throw it now?"

"Huh? This is really potent…"

"If they're bastards who kidnap children and try to starve old men to death, it's okay if they die from strong poison."

"Really? Let's see, the wind direction is… okay! Then which one should I throw?"

Tang Lan-Ah seemed somehow excited.

Qing could fully understand that feeling.

No matter how many blue practice grenades you throw, it can't compare to the thrill of throwing the real thing.

"Wasn't there only one?"

"I brought two just in case. One is spicy smoke, and one is deadly poison…"

"Good. Deadly poison, roger. Keep the spicy one for when we run away later."

"Hehe. I get to throw this. My brothers said to use it when we might become Public Enemies of Wulin if we mess up."

And immediately, the round object flew through the air.

"It's a Thunder Bomb!"

"Dodge!"

Thanks to someone shouting, everyone jumped and swam on the ground, causing a commotion.

Thanks to that, the poison bomb that fell to the ground without interference dropped with a thud and rolled to a stop.

The Namen Sect martial artists who were swimming on the ground blinked in bewilderment.

Qing asked in a hushed voice.

"What's this? Did it fail?"

"Uh, I heard it's supposed to be like this? They said the truly scary poisons are invisible…"

However, even Tang Lan-Ah's voice lacked confidence as she said this.

That's when the middle-aged man got up.

It was amazing reflexes, how he had jumped and lain on the ground so far away when he was in the center just now.

"You brats whose blood hasn't even dried behind your ears, how dare you mock your elders!"

He was beyond ashamed, having panicked and thrown himself at just a metal ball.

It was a cry full of anger, saying he would find and kill the bastard who shouted "Thunder Bomb" when this was over.

"Hmm. Is it something to brag about being old? There's an order even in dying, so when you see a Thunder Bomb, shouldn't the thought of covering your subordinates with your body cross your mind, old man?"

Since he asked if she was mocking him, she went all in on mocking him.

And the effect was tremendous!

"You, you! You gladly ignore the wine of courtesy and drink the wine of punishment!"

"Punishment wine is up!! The number one thing old bastards say!! Why on earth are old farts so desperate to force others to drink!! It's a mystery!! Looking for someone to drink the punishment wine instead!!! Seeking a pussy war- no, a black hearted warrior!!!"

Giggling sounds could be heard from behind.

There were even some among the Namen Sect who couldn't keep their composure and let out a snort before quickly covering their mouths.

"You, you! What are you all doing! Not cutting off that bitch's limbs and making her kneel before me!"

That's when it happened.

Thud. One Namen Sect martial artist just collapsed.

And then he convulsed, beating the ground with his whole body.

The expression 'having a fit' that's often used as a curse is actually short for 'epileptic fit', describing the state of foaming at the mouth and convulsing with the whole body.

He was literally having a fit in the purest sense of the word.

And the fit spread, with one after another collapsing and rolling their eyes back.

Then, bloody tears flowed from their eyes, nosebleeds from their noses, blood from their ears, and red-tinged saliva dripped from their mouths.

In technical terms, it would be called bleeding from the seven orifices.

Two eye holes, two nostrils, two ear holes, and one mouth make seven holes, hence seven orifices.

"Poison, it's poison!"

An even greater pandemonium broke out than before.

They scattered in all directions like insects under a rock, with some even heading outside the main gate, unable to distinguish front from back in their panic.

Qing's left arm drooped while holding the Moonlight Sword.

The sword of Nan'gong is the Emperor's Sword.

The emperor sits on the jade throne atop the imperial steps, looking down on all under heaven, moving millions of soldiers with a point of his finger. Hence, the strongest sword in the world reaches everywhere.

The space in front of Qing split diagonally.

The enemy's sword that got caught in that trajectory was pushed outward by the overwhelming force seeping through the diagonal contact.

With the weapon that should have protected the body flying out along with the enemy's sword, there was no means left to protect the body behind it.

The lower body fell to its knees, while the upper body flew and tumbled on the ground.

Following that, Qing swung her sword with precision, and swoosh, a long bloodstain was etched on the ground.

Qing smiled as she let her sword droop again.

She had thought the Sword Style suited her taste somehow since it entered her head.

It was a sword technique that observed and responded to the enemy's attack, drawing a straight line that minimized the angle of contact between weapons.

A sword technique that pushed away the opponent's weapon while cutting, so defense immediately led to attack.

It was easy to say, but responding after seeing the enemy's attack meant always giving up half a move and being at a disadvantage.

She could understand why Sword Friend stubbornly only used swords.

Dividing the front into eight directions for eight sides, dividing eight sides into sixty-four directions, and dividing sixty-four directions into a hundred for 6,400 straight lines.

It was a sword technique where you had to find the correct answer among these.

As such, how could there be time to be distracted by other weapons?

\textit{But, um, Sword Friend. Sorry for stealing the Emperor Sword Form.}

\textit{But I didn't choose it, you know?}

\textit{If you want to blame someone, blame my master, not me.}

"Alright. Next."

Qing said as she let her sword droop again.

It was what she said as she majestically blocked the main gate.

It was truly a moment when coolness exploded, with the spirit of a hero soaring high.

"Poison, it's poison!"

"Antidote- no, a physician- no, antidote first!"

"Brother, come to your senses, come to your senses!"

"You idiot, get away! You'll get poisoned too!"

Unfortunately, the Namen Sect martial artists affected by the colorless and odorless deadly poison were in no state to notice that coolness at all.

A win for Tang Lan-Ah.