\chapter{For Whom the Hammer Tolls (3)}

There's a saying about 'borrowing a knife to kill someone'.

It means using someone else's power to achieve an evil scheme.

He clearly knew the Namen Sect martial artists watching would come if he lit a fire in the furnace, yet he didn't say a word.

The old man snorted shamelessly.

"Hmph. What could I do? How could a country bumpkin who doesn't know martial arts deal with those bastards?"

"Aren't you being too brazen?"

"Weren't you the ones who drew swords? It wouldn't have mattered if blood wasn't shed, right?"

He was basically saying they killed of their own accord without him asking them to.

Qing spoke, dumbfounded.

"Well, we're Masters- no, I'm too much of a Master to be compared with those fodder, but anyway, since we're stronger, those scum hesitated. Otherwise, wouldn't they have caused trouble seeing pretty women?"

"A huge strongman, two extraordinary beauties, and one dreg walking around without a speck of dust on their clothes - I figured they must be formidable fellows."

The old man said, looking at Zhuge Lixian, Tang Lan-Ah, and Jian Buxi in turn.

And his final gaze turned to Qing.

"Oing. What's this. Why am I the dreg?"

"Why else would a woman cover her face?"

By the common sense of Jianghu, if someone covered their face, it was naturally because they had a face they couldn't show others.

Or it could be because she was a woman of noble status who couldn't casually show her face, but such noble ladies didn't lower their dignity by carrying swords.

"Anyway, I've seen a satisfying sight before I die, so I'll make the needle well. It'll be done soon, so take it and leave. They'll come swarming up in a frenzy since three of them died."

"Then what about you, old man?"

"What's the point of an old man living? They'll just use my useless grandson to pressure me. If I don't want to see that, I should just hang myself. Come to think of it, this needle will be my last work."

It was a miserable thing to say so calmly.

Qing frowned.

"What's this? You trying to evoke sympathy or something?"

"I have no intention of asking for help anyway, so don't concern yourself whether I hang myself or drink molten iron. I was barely hanging on before you came, planning to take down one of them before leaving."

Qing remembered the cold gaze of the old man quietly watching from the shadows when she entered the metal shop.

It seems his words about planning to take down one of them before leaving weren't a lie.

"Why don't you ask for help instead of thinking about dying?"

"Hmph. Who would I ask? Even other sects are all in cahoots, and the government takes bribes to side with them. Who could I appeal to for help?"

"Why, there are orthodox factions, you know. They literally use the character for ‘righteous'."

"Hmph. Orthodox or unorthodox, aren't they all the same Wulin lot? They're all just murderers with weapons. Isn't that what you do? If you want something, you steal and threaten, and if that doesn't work, you vent your anger. So what can you do? If you don't know martial arts and are weak, you have no choice but to just die."

Tang Lan-Ah flared up at this.

"What! You old man…!"

"It's fine. He didn't say anything wrong, so what."

As Qing restrained Tang Lan-Ah, Old Man Ban smiled crookedly.

It was a look that said, 'So how are you any different?'.

Well, he did say there were no orthodox factions in the city.

If the only Wulin practitioners he's encountered in his life were villains from unorthodox factions, they'd all seem the same to him.

In fact, just like how it is said that the interfering sister-in-law is more hateful, he might have hated the orthodox factions more for not caring while just talking about being righteous.

"It's a bit childish for provocation, but I'll bite. I'll look for your grandson, so don't die and wait."

"You're going to help? Hmph. Even if you try to bestow grace like you're doing me a favor, I won't make swords."

"Who asked you to make swords? That's ridiculous. Swords are things you use and throw away when they're worn out, not something you cherish just because you got a good one."

Qing uses weapons carelessly.

You could tell just by how she named them.

A regular sword is a Moonlight Sword, a half-sword is called a Hell Sword.

The Fushen-di was no different.

If there is an afterlife, wasn't she abusing the Fushen-di to the point where Ban Chi, unable to bear it in the afterlife, might return as a Jiangshi-Ban Chi to seek revenge while weeping tears of blood?

If she got another short staff later, it would become Fushen-di (No. 2).

"In return, I'll also run away if things don't work out, so if someone says they ran away because they couldn't handle the trouble, then you can hang yourself or stick your nose in molten iron and die."

Qing said this and turned around.

Just as she was crossing the front yard of the metal shop, a corner of her vision flickered as the Mission Window clamored to be opened.

Qing opened the Mission Window and then dismissed it without even checking.

It would just be a sudden mission anyway, and the content was predictable.

Help the old man, or rob him, or kill everyone with the Heavenly Slaughter Star, something like that.

"Sister, please calm down first."

At that moment, Zhuge Lixian grabbed Qing.

Only then did Qing realize her mistake.

She had always caused trouble alone in these situations, so she had forgotten she had companions.

"Right. I'll go play around for a bit, so you guys go to Kaifeng first. Don't worry about me. If it doesn't work out, I'll just run away."

"Come to think of it, you did the same in Luoyang. But Sister, do you know how hurt Elder Brother Peng was?"

"Huh? Why?"

"If you had just asked for help, Elder Brother Peng, myself, or even Elder Brother Hwangbo could have easily dealt with a mere unorthodox faction. But you just left abruptly."

Qing waved her hand dismissively.

"Well, you all had your own circumstances. And back then, it was my business."

"When I first met you then, I let it slide thinking that's just how you were, but Elder Brother Peng was grinding his teeth. I wondered why, but now I understand. Sister, you say we are close enough to call us siblings, but when it's actually needed, you draw a line treating us as strangers."

"Well, we are strangers. Just because we're close doesn't mean we're carelessly entangled. I take responsibility for my own decisions. Strictly speaking, I'm not even part of the Divine Maiden Sect, and my master told me not to hold back because of her."

At this, Zhuge Lixian visibly showed a hurt expression.

"If you really think we're close, you should at least invite us once. Not just announce ‘I'll handle my own business, so let's part ways here.'"

\textit{Hmm. Is that really something to feel hurt about?}

Qing tilted her head.

"But I'm already a Super Supreme Master at running away, so even my master said that if I'm determined to flee, no one under heaven could catch me. So there's no real danger for me, but if you come along, you might be in danger."

"This time it's your responsibility, right?"

"Huh?"

"So if you don't invite us and we decide to come along, as you said, it's not your personal responsibility, right? Then you don't need to worry about it."

"Does that make sense? Because of me-"

"Haah. Forget it. I'll follow Sister on my own, so whatever happens, it's all my decision."

"No, wait, why."

As Qing made a sour face, Tang Lan-Ah seized the opportunity to chime in.

"That's right. If Qing'er goes, I'm going too. If things get dicey, I have this too."

Tang Lan-Ah pulled out something round about the size of a fist from somewhere and proudly showed it off.

Zhuge Lixian's face turned pale.

"That… Do you always carry poison bombs?"

"Ah. Don't worry, it's fine. It won't explode on its own."

For reference, this was the same as the line that accounts for an absolute proportion of the last words of people who die from explosives.

‘It's okay, it won't explode.' And then, BANG!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The group strode boldly through Zhumadian.

The good thing about having Zhuge Lixian was that just asking for directions once was enough to set the route perfectly.

"It's to the left up ahead. And then it's the first main street on the right from the big square."

"Hmm. Are there any enforcements for speeding?"

"Pardon?"

"Just kidding. Don't mind it."

It was incomprehensible to Zhuge Lixian.

A joke was a joke, but Qing's confidence was so imposing that they were naturally barging in.

"By the way, do you have any other plans?"

"Of course I do. I always have a plan."

"May I hear your wise thoughts?"

"Hmm. We go and demand they hand over Old Man Ban's son?"

"…? Would they hand him over willingly? And it was his grandson, not son."

"Son or grandson, what's the difference? And if they don't give him up, we attack. We block the main gate, I'll be in front, you guys in the back. If the enemy doesn't come, Lan-Ah will cowardly throw hidden weapons to provoke them into charging."

"…?"

"If a Transcendent Realm Master comes out, Peak-Transcending Ximen Qing will face them. The end."

"I see."

Zhuge Lixian nodded and then spoke.

"Is it too late to back out?"

"I don't hold back people who want to leave."

"Couldn't you at least pretend to hold me back…"

If it were the usual Zhuge Lixian, he would have dissuaded her and turned back at this point.

However, having already experienced Ximen Qing as a person, he knew well that even if he tried to discuss more detailed attack plans, she was the type to say 'Then I'll go alone' and charge in.

Moreover, with her brimming with such confidence, there was also an expectation that she might have some other method.

Tang Lan-Ah didn't have much thought.

Just the idea of going to defeat bad guys.

It was the typical thinking of a newbie chick on her Jianghu outing debut.

At this point, one might suspect if a stupefying aura was emanating from Qing.

However, Jian Buxi was unaffected.

Because she originally had no thoughts in her head.

And so, finally, the main gate with the Namen Sect's signboard appeared before them.

Qing continued forward without stopping.

The guards lazily guarding the main gate spotted the group, and especially upon seeing Tang Lan-Ah's face, their mouths fell open.

As they approached confidently without hesitation, the guards thought they must be guests from somewhere.

Watching this, Qing thought, ‘Why are unorthodox faction bastards so desperate to show their nastiness starting from the gatekeepers?' She couldn't understand.

"What business do you have?"

"We're here to find Old Man Ban from Ban Family Metal Shop's son? Grandson? If you hand him over quietly, there won't be any bloodshed."

"What?"

"Go and tell them. I'm in a good mood, so I'll let them off if they hand him over."

Qing stomped her right foot and launched like a cannonball with the subtlety of the Yue Maiden Footwork.

She stopped abruptly in front of the Namen Sect martial artist, her left arm continuing forward to grab his collar and swing.

The man's body floated up, not quite clearing the wall but hitting the top, sending tiles crashing down as he fell and crumpled.

Qing spoke with a sour expression.

"Sorry. Seems like I lacked strength. With both hands I could have thrown you over."