\chapter{For Whom the Hammer Tolls (7)}

As Qing took a step forward, Duan Yunxiao crawled away with one leg and one arm.

Regardless, Qing picked up Duan Yunxiao's fallen sword and swung it a few times.

Excellent balance and a flawless blue blade; even after tasting blood it clung in droplets, truly deserving to be called a famed sword without lacki…

\textit{Blood?}

Qing bent her elbow and examined her forearm.

Blood was streaming from a wound split open to the depth of one finger joint.

No wonder it was stinging and throbbing.

But there was a subtle addictiveness to the pain, one could say. At this level, it wasn't bad.

Qing looked down at Duan Yunxiao again, blood dripping from her fingertips, and spoke.

"Hand over the scabbard."

"I-I shall give it to you!"

"I need it. Hurry up. I'm getting dizzy, probably because I'm bleeding."

After receiving the scabbard, Qing spoke again.

"No like, why bother an old man from a metal shop when you have such a good sword? Do you use dual swords? Is Wulin the same in that there's no normal person among those who use dual blades? I heard it's a symbol of social disorders."

"Th-that's not it. It's natural for any sect to covet such an ironsmit…"

"What? Natural? What a funny bastard. I suppose it's natural to kidnap grandchildren, sell them off, and cut off work to starve people to death?"

"That's…"

"That's why it's natural to die by the sword when you live like that. If you've committed crimes, naturally you should pay for them. Even if your head gets cut off here, it's a natural death, so when Yama, the King of Hell, asks why you died in the afterlife, answer that you naturally died because you were naturally meant to die. Got it?"

"Wait…!"

Qing strode forward with long steps.

Duan Yunxiao crawled desperately, but the mobility contest between two legs versus one arm and one leg was as different as a race between an insomniac rabbit and a tortoise.

Before he knew it, Qing thrust the sword right under his chin.

"Don't act ugly, just obediently offer your neck."

"Please, spare me, hiEEK!"

Qing raised the sword high.

Duan Yunxiao covered his front with his palm, but that was a defense technique only someone who had learned the White Hand Demonic Arts could do.

And then, Slash!

"Argh!"

A person whose neck is cut can't scream.

However, Duan Yunxiao, whose palm to shoulder was sliced vertically into two halves, could scream, indeed.

"You should have died gracefully, why harm someone else's arm? You reap what you sow, that's why you ended up like this."

His right arm was gone below the elbow, his left arm was split in two, and one leg was crippled.

Even if left alone for half a shichen, no, one ke, he would die.

Yet he tries to get away on one foot, hoping to live, but unless the heavens is moved by his sincerity and a cloud-riding Immortal appears to save him, he is already beyond saving.

Qing turned away without lingering anymore.

Although her arm was injured, she managed to pick up Moonlight Sword (No. 9), so she could just call it evens.

Moonlight Sword (No. 9) was longer and thicker than Moonlight Sword (No. 8), about half again as heavy, and its weight felt just right.

The metal shops that the Divine Maiden Sect commissioned weapons from made lighter swords for women to use.

Moonlight Sword (No. 8) was also made lighter than men's swords.

For Qing with her monstrous strength, it didn't even feel like she was swinging anything, making her wonder if this was how those ascetics with lightsabers in movies felt.

"What are you all doing? Everyone, kneel."

Qing spoke to the Namen Sect disciples who had been just watching.

In fact, kneeling was part of the basic training that Unorthodox Faction members learned as soon as they joined, so when the time came, it automatically came out as if ingrained in their bodies.

Seeing the disciples kneel without hesitation, Qing clicked her tongue and muttered loud enough for everyone to hear.

"Tsk. They listen so well. I thought I'd have to cut down two of them before they'd listen. What a shame."

It was a chilling sound for the listening disciples.

It wasn't for nothing that she spoke loud enough to be heard; with just one sentence, Qing had succeeded in gaining the upper hand.

At that, Tang Lan-Ah, upset that Qing was injured again, slapped her back as punishment.

Then she took out some cloth from somewhere and started wrapping it, saying she didn't have confidence in sticking needles into muscles that could block Sword Force, so this was the best she could do.

As she wrapped more and more bandages, the thickness of the arm increased in real-time, so Qing lost interest and shouted again.

"If anyone here sold Old Man Ban's grandson, raise your hand. I won't harm you if you come out willingly. I swear on my master's name."

An oath sworn on a master's name by an Orthodox Wulin practitioner is an unconditionally verified truth.

It doesn't work for Unorthodox Wulin practitioners because sometimes the master-disciple relationship is like that of enemies.

Although their actions were excessive, they claimed to be righteous experts of the orthodox faction in their words, so perhaps because of this, one person hesitantly raised his hand.

"Alright. Now everyone break their dantian. Begin. Oh right, those who say they're Peak Realm martial artists are exempt."

At this, one middle-aged man and two old men stood up with relieved expressions and quietly stood to one side.

For some reason, they had smug expressions on their faces.

"The rest can choose to give up either their dantian or their head. If you don't break it by the count of ten, I'll break your head myself. One. Two- Where are you going!"

Kneeling is a posture to show respect or submission, not to be used to gain momentum.

If you do, you have no excuse even if your neck gets pierced by a flying hairpin.

Even Tang Lan-Ah, who was wrapping bandages, reacted simultaneously, so two throwing knives were stuck as a bonus.

Crunch…

However, since the fatal wound was to the neck, the disciple who dared to attempt escape using momentum foamed at the mouth and crawled on the ground.

"Four. Seriously? I don't get it. Five. Do you die if your dantian breaks? Six. You're making a fuss even though I'm letting you live. Seven."

Even with a broken dantian, unless it's a special martial art, the muscles, bones, and wide-open meridians remain, so you're still left as a martial artist who can easily handle ordinary civilians who don't know martial arts.

Better than a Third-Rate who doesn't even know martial arts properly, but worse than a Second-Rate who can handle Qi a little, so if one had to classify, they'd be two-point-five, or in Zhongyuan numerical expression, Second-And-A-Half-Rate martial artists.

"Eight. Nine. Time's up. Let's see."

Qing looked around at the kneeling martial artists with shining eyes.

Each had a faint bloodstain at the corner of their mouth, so it seemed they really had broken their dantians without exception.

That's when it happened.

"This fucker bit his tongue and pretended to break his dantian!"

It seems someone was annoyed at seeing someone pretend to break their dantian without actually doing it, so a public informant appeared.

After Qing administered appropriate punishment, she took out a gold sycee from her money pouch, broke off half, and threw it to the informant.

"Here. You're free now. Go. You've got a lot of money, so leave carefully."

The public informant blinked, then with a loud 'Thank you!' quickly left the estate.

Qing didn't particularly try to stop him.

It was originally the case that public informants should receive appropriate rewards and protection.

Then she held up the remaining half of the gold sycee.

"Anyone need gold? If you report a bastard who didn't break their dantian and tried to sneak out alone, you get half a gold sycee. You've lost your Inner Qi, so you need some living expenses for a while, right?"

And then, lo and behold, there were two more such cunning bastards.

More precious gold sycees went out, and two informants left the estate with half a gold sycee each.

"Um. What should we do…?"

"You're Masters, so I can't just let you go carelessly. Maybe it's better to hand you over to the authorities. Lan-Ah, can you seal their acupoints?"

"Acupoints? Even First-Rates can just block that…"

"Then should we break their dantians first?"

At this, the three Peak Realm martial artists shouted.

"We won't block it!"

"We'll have our acupoints sealed and go to the authorities quietly!"

"That's what they say. Let them go."

And so the three Peak Realm martial artists had their acupoints sealed and collapsed to the ground with a thud.

That's when Zhuge Lixian whispered quietly.

"Sister, the authorities in Zhumadian are in cahoots with them anyway, so even if we hand them over, they'll be released soon."

"I know. But don't we need the excuse of the authorities for them to obediently let their acupoints be sealed?"

Some acupoints had mysterious effects like stopping bleeding with Inner Qi, paralyzing the body, sealing the mouth, or inducing sleep.

Ximen Surin had said her disciple should experience each one at least once and personally sealed her acupoints, but in Qing's experience, the most terrible was the sleep-inducing acupoint.

After all, when she woke up, she had a terrible headache.

If it weren't for that side effect, there wouldn't be any insomnia patients in Zhongyuan.

"As expected, Sister. When it comes to deceiving others, you're truly a master. This little brother can only continue to admire, admire, and admire again your vile schemes that utilize human psychology."

"Why is it that I feel like shit even though it's praise? Can't you just think these things to yourself from now on?"

"I apologize, Sister. But how can I, as an aspiring wise man, albeit immature, hold back words of admiration?"

In the end, he was saying he would continue.

\textit{What's this?}

\textit{Did I do something to upset Zhugie?}

Qing tilted her head.

"Alright. Only the one who sold Old Man Ban's grandson stays, the rest disperse. The party's over, time to go home."

Qing waved her hand, driving the two-and-a-half-rate martial artists out.

"Uh, Great Expert. What about me…"

"You're coming with us to find Old Man Ban's grandson. I'll let you go when the job's done, so don't worry."

"Ah, yes…"

"Now. Let's go. Sworn Sister, can you take care of them and come to the metal shop? Is that okay? If you don't want to, you don't have to."

Qing pointed at the three Peak Realm masters with sealed acupoints.

Understanding her meaning, Jian Buxi nodded with a dazzlingly bright smile.

"Ah! Yep! I understand!"

\textit{It's a bit of a waste to just kill off Masters at the Peak Realm level, right?}

\textit{I should feed the weak Sworn Sister living Elixirs to help her grow rapidly.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When they returned to the Ban Family Metal Shop, Old Man Ban was waiting with a rope tied to the ceiling beam.

"What's with this unpleasant interior decoration?"

"You're still alive, I see."

"The Namen Sect is gone now. I killed their leader."

At this, the old man's eyes wavered, then suddenly became urgent as he grabbed Qing.

"My grandson? Did you find him?"

"They said they sold him to the black market. We have the one who sold him here, so we're going to get a refund. Hmm? Is refund the right word in this situation? Zhugie, what do you call it when you go to undo a sale?"

"Wouldn't it be something like repurchase?"

There were still two months left until the Wulin Conference in May anyway.

It would be nice to go and play and wait, but it wouldn't be bad to use the remaining time efficiently.

"So put away that ghastly rope and wait. And tell us what your grandson looks like."

Life returned to the old man's fish-like eyes.

"Please find my grandson, Jagwon. If you find my grandson, I'll do anything. I'll make you swords or whatever you want, or I won't even refuse the position of weapons craftsman, so…"

"That's enough. What weapons craftsman? I don't need that."

"You don't need it? You say that because you do not know, but the work I made in my youth was the Xiqing Sword. How many sword craftsmen like me do you think there are in the world?"

"The Xiqing Sword!"

Zhuge Lixian shouted loudly.

Qing chuckled and spoke.

"Seeing how Zhugie is shouting, it must be some amazing famed sword. But you're an old man who said he'd never make weapons again… Why now? There must be a reason you refused to make them."

"That's…"

"Whether it's threats or favors, if you force someone who says no with that, what's the difference between the two? That bastard of a Sect Leader wasn't saying anything wrong. There's no reason to become the same kind of person."

The old man opened his mouth with a dumb expression.

Qing continued, giggling.

"I'll try making a scene if they say a refund, I mean repurchase, isn't possible, so take care of your health, old man. After all, if you're dead when we bring back your grandson, it's not like anyone can take responsibility."
