\chapter{For Whom the Hammer Tolls (5)}

The Namen Sect martial artists immediately started collapsing one after another, causing chaos.

Those with some loyalty cried out "Brother!" "Sister!" "Senior!" "Junior!" as they grabbed their convulsing sect members.

However, only physicians who were prepared could safely touch those poisoned by deadly toxins.

Among the Namen Sect thugs, even those with some loyalty who tried to help their comrades ended up collapsing and trembling alongside them.

Amidst this, Qing cut down about three enemies who rushed at the main gate.

After that, only those poisoned and having minor convulsions remained in the courtyard.

They had endured the shame of abandoning their sect's safety for their own survival.

It was like the story of Han Xin crawling between someone's legs, showing true potential as a chivalrous hero.

To think they would actually retreat inside…

One couldn't help but be amazed at the cunning of the Namen Sect martial artists.

"Should we set a fire? It hasn't rained recently, so it should burn well."

"A fire attack would be good. We've already used poison bombs, so why not add fire? But Sister, if a big fire breaks out, will Old Man Ban's grandson be safe?"

"Tch, why did he have to get kidnapped? It would be easier to just burn it all down."

"Hmm. Sister. Could you maintain just a little bit of dignity as a righteous female expert?"

"Hmm. I had intended to use this opportunity to eradicate these filthy unorthodox Demonic Adepts through a fire attack! However, I cannot bring myself to carry it out for fear of involving an innocent child, which is truly regrettable!"

"You can do it if you want to, can't you?"

Zhuge Lixian nodded with satisfaction.

"My lips are going to blister trying to maintain dignity. Do we really need to stretch out something that could be said in two words?"

"It's valuable because it's difficult to maintain."

It was persuasive, befitting the top intellect among muscle men.

The eloquence of smart people is frustrating but impossible not to accept.

"Alright. Let's go find that grandson. Since they've completely lost their minds, we can just beat them up until someone who knows comes out."

That's when it happened.

"You fools! Do you think colorless and odorless poison stays in one place forever! Where did you learn such manners, running away from the enemy! You, you, and you. The poison has already dissipated, so spread the word to gather again!"

"Yes, yes! Understood!"

It was an old man with a fierce expression full of wrinkles.

The Inner Qi in his voice was no ordinary thing, so Qing carefully sized up her opponent.

\textit{Surely another Unrestrained Realm Master wouldn't pop up, right?}

Meanwhile, the old man stood proudly among the corpses and soon-to-be corpses and spoke.

"This old man is Yu Qiesheng\footnote{余且勝. Yu Chaseung (유차승) in the original text}, a Disciplinary Officer of the Unorthodox Path. You must have heard of my reputation."

"The Blood-Forged Sword Demon!"

Zhuge Lixian shouted loudly.

Qing frowned.

She really couldn't understand why both allies and enemies always shouted out titles after hearing names.

\textit{Is it some kind of Jianghu common sense or custom?}

"Is he a famous old man? No. He must be famous since they shouted. Is he a strong old man?"

"He's a Great Demonic Adept in the Late Stage Transcendent Realm."

Zhuge Lixian couldn't hide his tension.

However, Qing's expression relaxed upon hearing those words.

"Ah. Then he should be manageable."

"Sister, did I perhaps say Late Stage Peak Realm? I must have misspoken. He is not a Late Stage Peak Realm, but a Late Stage Transcendent Realm Great Demonic Adept."

"You said it right. Late Stage Transcendent, right? I'm Ximen Qing, Peak-Transcending. Even Unrestrained Realm masters get crushed by me. Right, Lan-Ah?"

"Yeah. Yeah."

"You've defeated Unrestrained Realm Masters? No, Sister, why didn't you tell this little brother such an interesting story earlier? I'm hurt."

Yu Qiesheng's expression hardened as he watched this scene.

The purpose of revealing one's name in Jianghu was to gain the upper hand by showing off one's realm or backing.

Normally, with the Unorthodox Path and Late Stage Transcendent Realm, average Jianghu youngsters should be trembling and looking for a chance to run away.

But if they're casually chatting?

Yu Chaseung's mind raced quickly.

Come to think of it, colorless and odorless deadly poison wasn't something you could just go and buy anywhere with money.

Strong poisons have deep colors and smells, while those that are colorless and odorless are usually weak.

Poisons that satisfy both conditions are not easy to obtain even with a thousand gold pieces.

Moreover, the beauty of one girl was enough to stir lust even in an old man, so combining the two, a conclusion could be drawn.

"That girl over there, aren't you the Speaking Poison Flower of the Tang Clan?"

"Huh? Do you know me?"

Hmm. Yu Qiesheng swallowed a groan.

As expected, just as he thought 'what if', it turned out to be an affair entangled with the Tang Clan.

And then the youth with the mountain-like build looked different too. If it was the Young Prodigies gathered before the Wulin Conference, he must undoubtedly be the Beastly Sage, the heir of the Zhuge Clan.

The timing couldn't be worse.

The Wulin Conference was a united meeting for the Orthodox Wulin, so it was a time when they absolutely shouldn't give any pretext.

Isn't creating an enemy the best way to unite in the first place?

"Ahem. This old one is a Disciplinary Officer of the Unorthodox Path, here to confirm rumors that the Namen Sect Leader is concocting evil decoctions. I assume you are here for the same reason?"

Zhuge Lixian picked up on this.

"We were simply trying to rescue a child who was said to be kidnapped. But when you say decoctions, surely not…"

The Namen Sect Leader is a leper.

And an evil decoction made by a leper was something too horrible to even mention.

"Hmm. This is unfortunate. It seems the rumors are true, so I'll use my authority as the Unorthodox Path's Disciplinary Officer to expel the Namen Sect. So this old one has no more connection with the Namen Sect now."

Yu Qiesheng's conclusion was to cut ties.

"This old one must leave now. I am far too busy with urgent matters to linger in a place that has nothing to do with me."

As Qing was about to say something, Zhuge Lixian grabbed her shoulder and shook his head.

"Why?"

"The Namen Sect Leader is also a Transcendent Realm martial artist. Perhaps, are you confident in facing two Transcendent Realm martial artists?"

"Hmm. That's a bit… yeah."

Qing clicked her tongue and barked.

"You should know how lucky you are, old man. Be careful on your way at night. Next time we meet, you're dead."

Even if her face wasn't visible, it wasn't something an old man should hear from a young girl with such a green voice.

Yu Qiesheng forcibly suppressed the anger welling up inside him.

"The girl with the covered face has quite a rough tongue. Isn't it proper to reveal your name when saying such things?"

"My name is Ximen Qing, and my master is the Zenith Among Women. Happy now? Old man, next time we meet, you're dead."

"Ahem. It seems you have inherited that temperament as well…"

Yu Qiesheng internally rubbed his chest.

He thought he had done well to hold back, as he almost touched the disciple of the Female Mad Dog.

If she even passed on her surname, she must be no ordinary cherished disciple; rather, a walking human trap.

"Ahem. This old one will be going now. Would you mind stepping aside?"

-Is there really a need to pass this way? Can't you just jump over the wall? Don't bad guys usually like jumping walls? Thieves, robbers, assassins, arsonists, kidnappers, and even perverts with voyeurism. All those evil fuckers were jumping walls, though.

Qing muttered loud enough for everyone to hear.

Zhuge Lixian sent a reproachful look asking why she was needlessly provoking him, but Qing pretended not to see and played dumb.

Since she deliberately spoke loud enough to be heard, Yu Qiesheng could no longer jump over the wall.

Now, if he jumped the wall, he would become either a thief, robber, assassin, arsonist, kidnapper, or a pervert with voyeurism.

Yu Qiesheng forcibly suppressed his boiling blood pressure.

Trying hard to ignore her, thinking she must be a little mad dog, being the Female Mad Dog's disciple, he was about to stride through the main gate when…

"Ah. Right. Hey. Old man."

"…What is it?"

"Earlier, you said something about a woman with a covered face. I didn't cover it because I'm ugly, you know?"

"That is exactly what a woman with a covered face would say."

"Ha. Everyone is surprised when they see it, I tell you."

"What, are you pockmarked or something? If you are so confident, why don't you just show it?"

At this, Qing lifted her face veil.

Yu Qiesheng's eyes widened in surprise.

At that moment, Qing's right hand subtly reached out and gently grasped Yu Chaseung's wrist.

"What is this?"

Qing smiled mischievously.

Once you reach Late Stage Transcendent Realm, you don't usually let your body be grabbed easily, so she had startled him a bit, and it was perfectly effective.

"Have you heard of the Buddha's Palm?"

"Wha-"

In that instant, an enormous amount of Inner Qi surged up from Qing's dantian all at once.

It was an incomparably more intense flow than when she faced the Demonic Cannibal.

Not only had her Inner Qi increased several times since then, but with the addition of Overhaul Rebirth and the Yijin Cleansing Method, the flow through her Eight Extraordinary Meridians was also different from before.

As it was a Buddhist Divine Art, the Great Meditation Qi and Yijin Cleansing Qi took the lead, shouting excitedly as they rushed in, followed by the Zhu Xiang True Qi and the Daoist family members.

Seeing this enviously, the Demonic Qi peeked out, and the Yue Maiden True Qi, guarding the principle of the Golden Mean, nodded once.

Excited by a proper summons after a long time, the various True Qis bustled about noisily as they left the dantian.

Deng-!

A huge but far from noisy sound of a Buddhist temple bell.

Suddenly, a cloud of dust rose thickly.

Within it, Yu Qiesheng's grabbed wrist swelled, bulging flesh rising up his elbow and over his shoulder.

His entire body swelled, tearing his clothes, his head doubling in size, before suddenly returning to normal as if it were a lie, and he collapsed with a thud.

As the dust cleared, the wall behind where Yu Qiesheng had fallen, reaching about one zhang in height, had disappeared, leaving only debris.

It was the form of Cintāmaṇicakra, the Internal Explosive Qi Strike of the Buddha's Palm, used at full power for the first time in a long while.

Qing let out a tired sigh.

"Whew. My Qi is completely drained. Seriously."

"Sister? What is this…"

"Ah, this is called the Buddha's Palm."

"Why does Sister know the Buddha's Palm- Ah! Was this why you deliberately provoked him about the wall! There's no martial artist who would jump the wall after hearing those words!"

"Yeah. Once I grab them, a Transcendent Realm is no big deal. Even if they're prepared and we clash with Internal Explosive Qi Strikes, I can handle it, but if they're caught off guard, there's no answer to it."

"As expected! Inducing the enemy's carelessness and striking their weak point! What an excellently vile tactic! Sister, you always surprise this little brother!"

\textit{Wait, what? Is this praise?}

\textit{It's felt like he's been force-feeding me compliments for a while now.}

Even though they say Internal Explosive Qi Strike is an advanced subtlety, its essence was a method of crudely competing with Inner Qi.

That's why even with the Demonic Cannibal, she had to provoke him and roll around, sweating bullets trying to deplete his Inner Qi.

However, with her master's confirmation that she had Inner Qi comparable to the Unrestrained Realm, now Transcendent Realm was no big deal.

That's when it happened.

The Namen Sect martial artists finally swarmed back, led by a man whose face, hands, and all exposed skin were completely wrapped in bandages.

The bandaged man shouted with an urgent expression.

"Disciplinary Officer! We apologize for involving you in this unsavory affair… Disciplinary Officer?"

"Your Disciplinary Officer? You mean this?"

At this, Qing held up the (former) Disciplinary Officer, still gripping his wrist.

Suddenly, Tang Lan-Ah had a question about this sight.

\textit{Huh? Wasn't she unable to use her right arm?}