\chapter{When Mom Goes to the Island's Shade to Pick a Head (10)}

Strategist Bang Jeom-myeong, whose alias was Bang, belonged to the Nangogak of the Sado Alliance, or Sado-ryeon for short.

Nangogak, a gathering of the Sado-ryeon's brains, was named after that Nango, a ‘traitor's face'. Hence, even the name of this organization could be regarded as quite malicious.

Officially, it was said that the name was suitable for a strategist who walked the Sado path. Namely, a name that embodied strategies that didn't conform to the principles of justice, and the Sado spirit to eat their superiors and make a name for themselves.

However, if one were to look at how much the Unorthodox martial artists detested tacticians in particular, they would realize the true reason behind the name. Those who could barely throw a fist would act all high and mighty simply because they were a bit good with their heads.

Anyway, Bang Jeom-myeong thought.

This is really impossible, damn it.

After having such a thought, he felt a sudden pang of sorrow.

He couldn't even voice his lament, as he was worried that if he did, he might be caught, tripped, pushed, or harassed in the future.

That was how the martial artists of the Sado-ryeon treated their strategists.

"Why are you not answering? I said let's have fireworks?"

"If you mean fireworks, then……"

"It's a Wulin Tournament, so we should fire up some fireworks to show how awesome Sado-ryeon is, right? Don't just think of firing one or two. I want the night sky to be as bright as daytime! Do you understand?"

"T-To fire fireworks, we need permission from the authorities first."

"What? Why do we need their permission to set off fireworks?"

"Well, because of the gunpowder……"

"What? Are fireworks gunpowder? I knew there was that kind of smell. But so what?"

Gunpowder was an extremely sensitive matter.

Therefore, if civilians wished to set off fireworks, they would first need to give a large amount of gold and silver to the authorities. They would then have to request it through a proxy at the firework workshop in Beijing, smuggle out the amount of desired fireworks, and then ask the name of an official to set off the fireworks.

The bigger the scale, the higher the rank of the official they had to borrow.

If they were just shooting off one or two, they could use someone from the magistrate's office. However, if they wanted to illuminate the entire night sky, they would have to borrow the name of at least the police commissioner to avoid being implicated.

Therefore, they would need a huge amount of gold and silver due to the bribes, the cost of the gunpowder, and the bribes that followed.

That was the price to pay for setting off fireworks for just one night.

"Agh, why is it so expensive? But that also means we can raise the status of Sado-ryeon that much more, right? Let's try suggesting it. Be sure to write down that I said it, okay? What should I call it? Fire, I mean Spark? Ignition?"

"B-But the budget…"

"That's for the Nangogak to figure out. Isn't that why we have strategists like you?"

"Yes……"

The Southern Wulin Grand Assembly, shortened to the Murim Tournament.

It was the Sado-ryeon's desire that if the Orthodox Wulin had one, then they should have one too.

They had to do so as well.

If the Orthodox Wulin rallied together, shouldn't the Unorthodox Murim also rally together?

Of course, the preparations were entirely up to the working staff.

They should just let the working staff handle it. It was that there were several people who kept saying shit that wouldn't work, as if they were excellent ideas.

It was a transparent and obvious ploy.

They were just trying to get in the good graces of the Alliance Leader.

Later, if the Alliance Leader seemed satisfied, they could then say ‘Ah, that was what I had suggested! Haha, the fireworks, doesn't it show the true spirit of the Sado-ryeon!'

The Sado-ryeon's Alliance Leader, a peerless martial arts genius, was not only the greatest when it came to her own martial arts, but also in teaching others.

It was said that simply by observing and casually making a comment, the person receiving the comment would immediately have an epiphany.

The fact that the Sado-ryeon's close aides had made great accomplishments in just a few years proved this to be true.

Therefore, everyone had no other choice but to do their utmost to get in the good graces of the Sado-ryeon.

"If you take out my name, I'll seriously kill you."

With a threat that sounded like something a child would say, a Sado-ryeon Elder patted Bang Jeom-myeong's shoulder, or rather, struck it hard according to the frail strategist, and left.

Bang Jeom-myeong could not even sigh. As he silently swallowed his frustration – ‘Fireworks my ass, what in the world do you want me to do' – the door of the Nangogak burst open and another Elder appeared.

"Oh, Strategist Bang. You're working hard. I just had a good idea."

"Ah, yes."

"The Orthodox bastards are setting up a martial arts tournament stage on top of the canal, yeah?"

"Uh, since the Dongting Lake is too far north…"

"No, man. You have to listen until the end. Now that they're setting up a stage for a water tournament, it'll only sound like we're copying them. So what we'll do is to build an aerial tournament stage! We'll build a high tower and make them fight in the sky!"

"Then, how about the spectator seats……?"

"Just build them higher!"

"But how do we……"

"Why are you asking me? You're the one who should think about that from now on."

Bang Jeom-myeong's shoulders drooped.

Damn it, this is impossible, damn it.

It was then.

"Ah. Right. Here."

The Elder suddenly handed over a well-made box.

When Bang Jeom-myeong opened it, inside was a writing brush made of marten hair lying on silk, a truly valuable treasure for a scholar.

"Oh, are you giving this to me?"

"I'm not the one giving it. Seems you had some ties in Guangzhou? The Sect Leader of the Salwol Sect sent this as a gift for your son, it seems?"

At this, Bang Jeom-myeong just blinked his eyes.

"I've never visited Guangzhou in my life, but are you sure? I know the name of the Salwol Sect, but I have no ties to them at all."

"I don't know. Seems like they're trying to make some kind of connection with Nangogak. Wow, Strategist Bang, it seems you have people lining up for you, huh? Are you going to take flight soon?"

And then, he smacked his shoulder hard again. I don't know why people were all patting his shoulders but they were practically breaking it.

Bang Jeom-myeong gazed down at the valuable brush.

It was from the Salwol Sect, right?

Why specifically me, who is at the bottom of Nangogak?

He did not know the reason, but it was a valuable brush so he was thankful, and also he was even more grateful that it was a gift for his son.

Since he had no way to repay him, he thought to secure a good spot for him at the Wulin Tournament.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Just as the Guangju Merchant Guild was an alliance of related trading companies, the Geumjeok Gang was also an alliance of loan sharks and thugs.

And when the loan sharks of Guangzhou were wiped out, everyone was too busy watching the Tapping Beauty's knife dance, or rather the hammer dance, to care.

So it was only upon seeing a row of coffins that they thought, what, why the hell did those guys all die at once?

It was a sense of bewilderment that contained a lot of regret and disappointment.

If they were to die, they should have died with a time difference.

They were busy celebrating that the Guangju Merchant Guild had died!

If they had died three days later, they could have enjoyed the celebratory atmosphere while chewing and tearing at the bones of the dead as snacks.

As such, the people of Guangzhou had so much to say that their tongues and lips were practically chapped.

But still, why did those money lenders die?

It had to be a curse, a curse.

The Divine Maiden was certainly skilled. While the Merchant Guild bastards went down when she was physically present, the Golden Bastards were wiped out by a curse.

And that curse returned to the Goddess Shrine.

With a casual demeanor as if entering her own home.

"Wow, Mom, you're really fiery, aren't you? Is it okay to just kill them like that in the open?"

"What? Weren't you going home? You suddenly appear again after not showing your nose."

"Eii, you told me to live a good life, right? So this good son did some good deeds and returned. But Mom, you really have big hands. I was cautious of accidentally killing innocent people, so I would thoroughly investigate before cutting throats, but Mom, you simply kill them all without question."

"Why leave anything behind when cleaning up garbage?"

Qing suddenly trailed off.

After all, something felt off and didn't sit right with her.

It was a feeling that was starting to become clearer.

It's strange. Why was everyone I killed a bad guy?

Why were all the ones she killed bad guys?

Even when they had faced those mountain bandits, there were less evil bastards with double-digit Evil Karma, who were spared.

But why?

Even if the Guangju Merchant Guild was that cruel, how could every single one of them be a bad guy?

She even heard that they were heavily recruiting disciples and spreading various elixirs while hindering the Jin Clan's disciple recruitment.

If that was the case, the prospective recruits, the first, third, no, maybe fourth generation of newbies, should not have been that evil, right?

Was it like those Caucasian gangs where they needed to kill someone innocent to be accepted into the organization?

Well, how different would the way evil people recruit new members be anyway?

Or perhaps, the numbers I see… No, no. Bad thoughts. Bad thoughts. Let's only see good things, and only think of good things.

Good things, like my pretty sworn sister's face, my sister's huge chest, and my sister's huge chest that I can rub as much as I want. Oh wow, so exciting.

"Kyahaha, it tickles. Sis, you really like my chest."

"No one dislikes breasts, okay?"

At this, Yeom Hwiyoung's eyebrow twitched.

"Hmm. Should I also start calling her Mother instead of Aunt? I do appreciate all the love, but shouldn't you be more restrained in front of your son?"

"Well, anyway. I think it's admirable that you carefully investigate before punishing evil. Keep doing that."

At that, Yeom Hwiyoung's face bloomed.

Although his smile was not a scene she particularly wanted to see.

And then, he suddenly knelt down on one knee in front of Qing.

"What is it?"

"Are you only going to praise me with words? It's not a very profitable business to just give compliments like that, is it? If you keep acting like this, your son might become spoiled, Mother?"

"Then what if I don't just praise you with words?"

Instead of answering, Yeom Hwiyoung just stuck out the crown of his head.

Qing's expression soured instantly.

"Agh, seriously. You are something else."

Although she wasn't particularly inclined to do so, it was probably better to give him what he wanted.

After all, it was admirable that he carefully investigated and killed the bad guys so he wouldn't kill someone innocent.

Since she was the only one who could see Evil Karma and he was just an ordinary Master of the Transcendent Realm, how large of a disaster could occur if he went astray?

Therefore, she had to sacrifice herself for the peace of Wulin.

So, with an unwilling expression, Qing gently patted the head of the son wannabe.

Fortunately, the soft, weighty, and supple feeling of her breasts were squishing against her left hand, which balanced out her right hand's unpleasant feeling, making it more or less a zero sum game.

"I'm telling you now, I'm not praising you because you killed bad guys. That's just something that you should do by default. I'm saying that your effort in differentiating between bad guys and good guys is admirable."

"Yes, Mother."

As soon as he said that, he suddenly grabbed her hand and rubbed it against his cheek. Qing, shocked like a cat thrown into water, leapt back.

At that, Yeom Hwiyoung giggled.

"I'll continue to be a good son, so how about you just get used to it, Mother?"

"Seriously, I'm going crazy……"

Qing looked at the son wannabe who said that.

Was this an example of a Transcendent Realm Master, who, with nothing else to do, would act mischievously and tease a junior in a family roleplay because of their physiological needs?

Or was it the true him?

It was impossible to know.

Perhaps the former was better, but as for the latter… hmm.

Of course, she had seen it back in the formation; a distorted mother of the Supreme Leader wannabe.

She had never seen her mother smile a single time since she was born, so all she ever saw was the hatred in her eyes, which was why, even in his hallucinations, the ideal image of her mother was one that loved him.

Ugh, just thinking about it gives me goosebumps.

Even so, was it even possible for a stranger, especially a young girl, to follow her around as her mother?

It didn't make sense logically.

But with those eyes, filled with overflowing affection, as well as the awkward smile that didn't shake off the fear, it made her wonder.

Please love me. Please don't throw me away.

When he had first approached, his eyes seemed to shine with a dangerous glint, but why did he suddenly become like a docile, large dog?

Was it after giving him a name?

Though it was a large dog with a terrible attitude.

And so, the soft-hearted Qing had no other choice but to be lenient.

"Alright. You should just keep the whole ‘Mother' thing on hold for a while. The Tapping Beauty has left, and the Heavenly Flower Sword remains."

"Ah. So you're going to disappear like that, huh? Then, oh well. It cannot be helped. Have a safe trip. This good son still has some good things to do."

Qing cocked her head.

What's with this? He's withdrawing so easily?

She thought he would have thrown a tantrum.

That she didn't have the right to call his mother ‘Mother,' or that he would childishly demand to know when he should start calling her Mother.

But it seemed Qing had underestimated the Master who had reached the Transcendent Realm, after all.

Moreover, he was a Master who had long ago reached the Transcendent Realm and had been intentionally delaying the completion of his realm in order to receive the Heavenly Demon Spirit.

Although his words were light and his attitude even lighter, he was not actually a light person.

When he said to keep the whole ‘Mother' thing on hold for a while, it was also meant that he would do it later. That was an indirect confirmation that he would eventually call her Mother.

As such, Yeom Hwiyoung just smirked with satisfaction.