\chapter{When Mom Goes to the Island's Shade to Pick a Head (1)}

"Whose son is that? What a loud voice." Qing mused.

Having no son of her own, Qing just thought he must be someone's son who had gathered here. It seemed he was a very filial son. Perhaps a son who had been away for a long time had returned?

When Qing craned her neck from her position being carried, she saw a well-dressed young man with an eye patch approaching. Their eyes met, and the young man immediately broke into a smile of pure and utter happiness.

Qing tilted her head and looked behind her. The prospective guests of the shaman's house were all looking on with great expectation and glittering eyes. Yet none of the women looked like a mother happy to see her son.

"What is this? Huh." Qing was shocked when she turned her head back.

The young man who had been some distance away was now right in front of Gyeon Pohui. He immediately prostrated himself on the ground, showing the crown of his head.

"Mother! Your son greets you!"

Qing blinked a few times, confused.

Then, a thought struck her, and she asked in a trembling voice of disbelief.

"Did you say… ‘Eume'?"

"Yes."

"Are you… my nephew?"

"Yes."

"You said you weren't a mother, right?"

"Yes."

Yes wasn't enough! Surely, some other explanation was required?

Qing changed her line of questioning.

"Wait, who is this… no, who is this person?"

"My nephew."

"Your adopted sister's son?"

"No?"

"Then, did you perhaps adopt another sister?"

"No? You are my only adopted sister."

The conversation had fallen into a bewildering labyrinth.

It was starting to feel like she was answering the sphinx, so Qing directly asked a blunt question.

"No, then, whose son are you?!"

"Your adopted sister's."

"But I'm the adopted sister."

"Yes. My adopted sister. My adopted sister's son."

"My son?"

"My adopted sister's son."

Qing's expression soured.

What in the world was this about?

After her ‘adopted sister' persona, was this the "I'm-Your-Son" persona?

Of course, her adopted sister was quite earnest, so Qing had eventually selected her as her official adopted sister.

"Excuse me? Who… Who are you to call me mother, Ah, what in the world is going on?"

"Mother! It is I! Me! Your son, um… It's me!"

It was a young man without a name.

Since he couldn't find a proper noun to reveal who he was, he simply repeated "It's me."

Qing was exasperated.

"No, it's not ‘Mother' you should be saying, you'll bring disaster on yourself if you keep saying that."

At those words, despair filled the young man's voice.

"Why do you not accept me! You clearly told me to live kindly, to live kindly and wait, and that we would meet again and you would come to find me!"

The young man's voice was heartbreaking.

The sorrow, despair, and resentment in his words made the onlookers whisper amongst themselves.

- Look, look. Isn't this just like what we've heard?

- If one sleeps with a woman a hundred nights, she'll surely come to find them.

- It seems the Earth Spirit has the power of a god, but no maternal love. Did she just abandon her son and pretend not to know him?

"Geez. I'm going crazy. Look, just who are you? Have we even met before?"

"Am I so different that you do not recognize me! It is I! Me, uh, it's me!"

"No, not ‘It's me'. Who are you?!"

"I have not received a name, so I cannot reveal a name to you! You have yet to bestow one on me!"

A brief silence followed.

Then the whispers resumed.

- What? She hasn't given him a name?

- Wow. She's harsh, she's so harsh. She must be that harsh to defeat curses. So strong.

- To come all the way here to find his mother who didn't give him a name? Wow, if I were him, I would have treated her like my mortal enemy.

- But still, it's his mother. What could he possibly do? Once you grow up as an orphan, nothing would be as dear to you as your own mother.

"What are you all? Storytellers? Can you all not be quiet? Do you want to taste my powers?"

Qing tried to scold the crowd, but her words had little effect.

It was then.

"Hero!"

A young girl, around ten years of age, popped out from somewhere, grabbed the young man's shoulder and struggled to get him to stand.

"Stop it! Why are you kneeling, Hero?! Madam Spirit, you're too much! How can a mother abandon her own child like that?!"

"I'm seriously going crazy……"

"Even if Madam Spirit doesn't know, the Hero saved my mom and me! He must have done it because he was thinking about his mother! That's who he is!"

The young man attempted to protest.

"No. That was just because some bad guys were there, and I was just trying to do some good-"

"Shut up! What would you know, Hero Oppa!?"

"? If I don't know my own affairs, who would-"

"I'll kneel too! Mother! Please accept Hero Oppa! Please!? If you at least live together, you'll surely become fond of him!"

Then, she knelt next to the young man and bowed to her, as well.

Qing's eyes began to twitch.

What in the world is this?

Following the "I'm-Your-Son" persona, now there's an "I'm-Your-Daughter-in-Law" persona?

Why do all of my family relationships all try to happen without my consent?

A 'sister' persona, a 'father' persona pretending to be a grandfather.

A 'mother' persona of a Queen.

And now, even a 'son', bundled together with a 'daughter-in-law'?

While Qing was at a loss for what to do, the crowd, emboldened by the daughter-in-law's valiant efforts, responded with great enthusiasm.

"Accept him!" "Accept him!" "Accept him!"

As if they had all been prepped to say it at once, they began to chant those three words in unison, and before she knew it, the voices had spread to the entire crowd, ringing out loudly.

"Accept! Him!" "Accept!! Him!!"

"Ah, it's not as if you're asking me to give up a prize or something. Why are you asking me to accept a child?"

A prize would be better than this.

At least with a prize, they were asking to give an actual item.

It wasn't to adopt a random person.

It was even more so when they were acting like they were trying to sell me a product at some event.

And the cries of "Accept Him!" weren't just coming from that one group of people.

"Ac-cept him. Ac-cept him."

"Eume, are you going to do this too?"

"But, my nephew was so nice to me. I like him, too. If only my adopted sister agrees."

"……Haaaa."

Qing let out a long sigh.

Then, she looked at the Righteous Karma of the young man, which had reached twelve points, and sighed again.

He wasn't a bad guy, but what is he?

If he was hanging out with her adopted sister, was he perhaps another one of the oddballs?

"For now, let's organize the facts."

The whole town seemed to have come and gathered, making the area in front of her door into a marketplace.

First, she should handle the rumors.

"I do not have children, and I have never been married. You're not saying that you came out from my stomach, right?"

"That is correct. However, as not everyone who comes from the stomach is a child, not everyone who did not come from your stomach is a stranger. You, too, are not siblings by blood of the same womb."

"That's why we're called sworn sisters. Did everyone hear that? He's not my actual child. I'm not even old enough to have a grown-up child like him. Don't you see that? What are you all looking with your eyes for?"

At that, the crowd awkwardly averted their gazes.

On one hand, she felt slightly wronged.

How can you tell if I'm some old or young shaman when I'm wearing something like a beekeeper's veil on my face?

"Second. Have we ever met before? Did I even promise to make you my son in the future or something?"

"Yes. It was three years ago, during the summer. And you scolded me and told me to live kindly."

"Three years ago? Summer?"

Qing tried to recall the memory.

Wasn't that when she was kidnapped by the Demonic Cult?

It did seem like she recognized the young man's face, but at the same time, she didn't.

The young man continued.

"In that moment, I was born anew. Isn't it only natural that the one who gave me birth would be called Mother? Thus, I am your child."

"What about my intentions……?"

"But you did promise. You clearly promised that you would accept me if I lived kindly. So I lived kindly. My adopted sister will bear witness to this."

"Yes. Yes. My nephew is very kind. I like my nephew. If only my adopted sister agrees."

"Ah geez. Another mystery. Alright, let's go inside and talk. Everyone, did you hear? If you spread rumors that I abandoned my child or some other nonsense, I'll bestow my curse on you!"

At that, the crowd lowered their heads.

They had been shouting with great momentum, but now they realized they shouldn't dare to talk back to the powerful Earth Spirit.

Moreover, after hearing the details, it was clear that she wasn't a heartless mother who had abandoned her child.

Instead, it looked like the young man was unilaterally begging her to take him in as her son.

It was only natural that a single old maiden, who was yet to be married, would be shocked to take in a grown adopted son.

"Let's go inside. Let's talk inside."

"Yes, Mother."

"Agh, I said I'm not your mother yet! And what about you? Why are you trying to get involved?"

Qing said, looking at the young girl.

"I have already been given grace by Hero. I was saved, and not only my life, but my mother's life as well. So since I have nothing, I'll repay the kindness with my body, with my entire life."

What a bold little brat.

Qing then looked at the young man.

The young man hmmmed, and then shook his head.

"Sorry, no, I'm not sorry, actually. Little brats with a milk smell still on them are not my type. If you're done with what you came for, then go. I appreciate you taking my side."

"H-How can you be so mean! You're truly too much!"

It was the moment the girl's first love was shattered.

However, if her daughter-in-law had been someone older than her, her parents probably would have objected as well.

The little girl covered her face, burst into tears, and ran off.

Qing cocked her head.

By the way, that flexible and gentle demeanor, it's like I've seen it before, but not really…

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was surprised at Gyeon Pohui's new beauty.

"Wow, your beauty… What's with your beauty? Eume, you've become so pretty! I might not have recognized you if you weren't veiled."

"Hehe. It's all thanks to my nephew."

However, even though the words that followed were not about her beauty, they were something to be concerned about.

"You! Alleged Supreme One!"

"Ah. Is that so. I heard you called me that, Mother. ‘Alleged Supreme One'… it's a rather interesting term, isn't it?"

"You… uh, how? Why, why have you become a Daoist Immortal?"

"It's because you told me to live kindly. Or rather, you told me to live kindly. And that, we would meet again with smiles on our faces."

Clearly, the Alleged Supreme One, who had a confirmed four-digit Evil Karma when she had last seen him?

Righteous Karma of twelve?

What in the world had he been doing all this time?

Qing's shock did not stem solely from the fact that a villain had turned over a new leaf, or that it just so happened that he was now begging to be accepted as her son.

If that was the case, was he actually a kind person now?

Could Evil Karma, more than one thousand points worth, be replaced with Righteous Karma?

Of course, before him, there was Gyeon Pohui, and there was also Choi Leeong.

But Gyeon Pohui was a simpleton who didn't quite understand the concept of good and evil, and Choi Leeong was just an empty shell, only having regret for his past.

But this guy?

He was a bastard who had such massive Evil Karma.

By simply accumulating Righteous Karma, could he become a good person?

"How……?"

"Are you referring to my appearance? I've undergone the Transformation of Reverted Youth."

"……?"

Suddenly, her dazed mind snapped into focus.

It seemed she had just heard something that she shouldn't have just let slide by.

"Transformation of Reverted Youth?"

"Yes. When one reaches the Transcendent Realm, the age of the physical body gradually goes back to the past."

"No, I know that too. The Transcendent Realm? But didn't I break your dantian?"

"You clearly told me that I could reach the Transcendent Realm if I were to just make up my mind, did you not? I was merely suppressing my realm. So, I reached the Transcendent Realm instantly and used the power of Transformation of Reverted Youth to restore my dantian."

"Oh, um. The Transcendent Realm."

What the hell? How is someone of the Transcendent Realm suddenly appearing before my eyes?

People didn't know just how powerful of a realm the Transcendent Realm was.

This was because they had no opportunity to experience it, nor would they have the chance to witness their martial prowess.

But Qing had been trained by the unavoidable nuclear noogies that ignored defense and the protection of True Qi.

The Transcendent Realm wasn't just a person.

It was more like a natural disaster or a calamity wearing human skin.

Qing became polite.

After the Extreme Sword Peak(truncated), it was the first time she showed her true nature, the classic act of being strong against the weak and weak against the strong.

And the Alleged Supreme One grinned.

This scent, no, this is my Mother, isn't she? This scent, this scent of fear.

And no matter how much he changed, he couldn't change his core nature.