\chapter{When Mom Goes to the Island's Shade to Pick a Head (4)}

Upon hearing that a name has been decided, the son-pretender lets out a playful exclamation, "Ooh."

However, despite his easygoing demeanor, his swallowing nervously and looking at Qing's eyes shows that he is trying his best to hide his tension.

"Hwiyoung. Yeom Hwiyoung."

"Ooh, it's an even better name than I expected? It's also not a common name. What does it mean, Mother?"

"Hwi, meaning to shine, and Young, meaning to be at ease. I hope you will become someone who is at ease even when you shine."

"Hwiyoung. Hwiyoung. It's Hwiyoung."

The son-pretender, Yeom Hwiyoung, repeated his name several times.

Like a food that didn't sit well, as if he felt awkward like a child with a toy that he had never owned.

"But isn't a name usually made like that? You're supposed to wish that they become a strong person, a high person, a noble person, or someone difficult for others to mess with, aren't you?"

"Why, should I have made your name "Cucumber Three-Eight "?"

It's one of the ways of naming a child in Zhongyuan, taking the last digits of the father and mother's ages.
The advantage was that there was no chance of forgetting one's child's age.

"That's not it. It still sounds like you're asking me to be a good person. Should I become a more ‘good' son here?"

"I said, a comfortable person, not a good person. What's so difficult about becoming a difficult person? People are usually hard to approach once they become great. Isn't it hard to be around someone even when they're just a Master who takes things so seriously and with a heavy weight? Those who are difficult, you cannot carelessly approach them, and, at the same time, they can also not easily approach you either."

In fact, it was more difficult to be a comfortable person, while also being a shining individual.

How great a word was comfortable?

Comfort when the body was light and at ease, comfort when the mind was at rest, or even a word that included ease of preference and a light approach.

Wasn't it a word that was filled with all kinds of peaceful feelings, such as good, cozy, easy, and relaxing?

So, people would easily approach and extend a hand to a comfortable person, smiling and greeting them with joyful eyes.

Because they were comfortable. Because they were comfortable people.

"……In other words, a comfortable person is someone who is loved by everyone, you know. It's not like you've received much of anything until now, so I named you that so you can at least receive a lot from now on. Okay?"

Last night, when I was lying down in the bed, hugging Gyeon Pohee, it was so comforting.

And also, the bed was originally a very mystical place where the best ideas would occur just when drowsiness started to creep in.

As I was snuggling inside the warm embrace of my adopted mother, it made me think, ‘Ah, comfort is truly a great thing.'

"Hmm. I do not agree at all. To become a comfortable person. Isn't that basically asking me to become a pathetic fool?"

"What? So you don't like it?"

Yeom Hwiyoung smiled with satisfaction.

"No. I like it very much. Regardless of the meaning, you, Mother, painstakingly chose a good name for your son, and that's what matters, you see? It's all your heart that wishes for your child's well-being. That's what I've been wanting my whole life. Thank you, Mom."

"Ack, I told you not to do that!"

Qing shuddered and rubbed her arm vigorously.

The fluff on her entire body stood up, starting a general uprising, saying they couldn't live like this.

"I'm serious. Though the meaning doesn't resonate with me all that much, if you made a great effort to choose a good name for your son, then even if it was ‘yeombyunghal', then what would it even matter?"

At that, a vein popped out on Qing's forehead.

"I made such effort to give you a name! Why must you throw a damper on things like that? I gave you a gift, and you say you like it because you recognize my sincerity, even though you don't like the gift itself?!"

"That feeling, the heart, is what's important to this son, Mother. Now I was wondering if I should start trying to act cute and put on an act, after fifty years of not being able to do so. Would fifty years be okay?"

"Do people usually act cute for fifty years?"

"Then how many years should it be, Mother?"

"Hmm, I'd say, even if it's long, it should be finished within twenty years?"

"Excellent. So you're saying twenty years is okay, right? Mother, just tell this son. Right now. Is it that Soul-Crushing Sect or whatever? Those bastards are making you worry, right? Should I go and deal with them all?"

At that, Qing turned serious and shook her head.

"Don't say such things. I won't stop you if you say you want to act like a son, but that doesn't mean I will use you to control things just because I have a Transcendent Realm son. If my son is over fifty years old, then he should leave his parent's care and follow his own path, that's more than appropriate."

Yeom Hwiyoung's smile deepened.

Although he felt like he had been outmaneuvered, Qing had cut the line so clearly.

"I won't even think of ordering you around, so just go on your own way, got it? Why do you have to live with me for thousands of years like mother and child?"

"Yes. I love you, Mother."

Qing shook her head at that.

"Didn't you hear me? I said, ‘Go your own way', alright, go on, go on. Adopted Sister, bring me some salt, quick. It seems like the energy here isn't good. I'll sprinkle it so much that I make a salt farm."

"Huh? Then, should I bring about two hundred geun? Then, how many carts will I have to bring? One gama is ten mal, and three mal is forty geun, so a hundred geun would be about… Uh, three, six, forty, uhhh…"

Gyeon Pohee diligently counted with her fingers, adding and subtracting, and finally smiled brightly and said,

"I don't know. Will two gamas be enough?"

"You only need about a dipperful, okay? There's an evil spirit I just want to get rid of, so I'll just sprinkle it on them."

At this, Gyeon Pohee shook her head.

"Sworn Sister. You can't do that. My nephew will be upset."

"Indeed, I knew that my aunt was the only one who cares about me. My aunt is the best."

Qing also shook her head.

I just want all of them to fuck off.

This was Qing's honest feeling.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since the public's opinion in Guang Zhou had changed because of the son's unexpected actions, it was time to call people and properly start the reconstruction of the Manor.

The reconstruction of the Jin Clan Manor wasn't something that I was paying for, so naturally I needed permission from the people who were paying.

Qing went to find the Jin Clan Lord, Jin Jagang, because she thought it was about time to put up hiring notices and select a master carpenter.

As it happened, Jin Jagang was swinging his arms and legs in front of the Clan Lord Hall (his Tai Chi form was really out of shape), digesting the breakfast he had eaten.

Jin Jagang was bewildered by Qing.

Her group had increased, and while he could accept the youth who carried poison, the sight of her clinging to the veiled woman while having legs that were perfectly fine, made him go speechless.

Also, from the looks of it, she looked so at ease that she was even used to it. It was all too natural.

"Lady Heavenly Flower? Are you not feeling well?"

"Ah. Adopted Sister. Put me down. In front of elders, I have to put my feet down and greet them. This is my adopted Sister, Gyeon Pohee. She likes carrying me around. It's not that I want to; I just have to be carried, you know? Right?"

"Yes. Yes. Hello? My sister is imposing herself on you."

The two women gave their greetings.

"Who is this young man?"

"Ah, you don't need to worry about him."

Although Gyeon Pohee's aim was to attend to Qing, Yeom Hwiyoung had nothing else to do, so he just followed her to see what his mother was up to.

Yeom Hwiyoung seemed to ponder for a moment, then bowed his head respectfully.

"Hello. I am Yeom Hwiyoung, an unknown traveler. I've heard that my mother is here in Guang Zhou, so I have come here despite my rudeness."

"Did you say mother?"

"Yes, Clan Lord. The Lady Heavenly Flower here is my adopted mother."

"……? Lady Heavenly Flower? A son who's already this grown? Oh, um. Perhaps there is a reason for your, um… Lady Heavenly Flower's, umm, situation. That umm, is… a truly commendable son you have, yes?"

Although he looked shocked, Jin Jagang answered respectfully, since he had received respect.

He was indeed a gentleman with excellent character.

"An adopted son, no, a pseudo-adopted son, isn't it?"

"Ah. A pseudo-adopted son. I see."

Pseudo-adopted son meant the adopted child of a family relative, a child by blood.

When a complete stranger was adopted into the family, they were referred to as a pseudo-adopted child, or more widely, a ‘adopted child.'

He looked very curious but did not probe further, which was also a testament to Jin Clan Lord's character.

However, Yeom Hwiyoung's mouth did not remain silent.

"Originally, I had a vicious personality since I was young and have lived committing many crimes, but when Mother scolded me, this evil person of the past repented and was born anew, which is all the same principle as the great cycle of life. So this son is asking you to let me serve my adopted mother."

"Ah. That's. Um. A tale of virtue. A tale of virtue……..is it?"

Jin Jagang was in a state of confusion.

A vicious man repented and became a new person, and thus he asked to serve his adopted mother.

If Qing was around forty years old and was a mature adult, it would be a great tale about a great figure who guided an evil person to goodness and that evil person being moved by it, wouldn't it?

A heartwarming tale that was almost out of the historical records.

But, no matter how he looked at it, it was a bit strange for a young man probably in his mid-twenties to refer to a girl who had just turned twenty-one as his adoptive mother.

And if he called a woman younger than her son, ‘mother', then that would become a story only gossipmongers would relish.

And that confusion spread to the Jin Clan.

"Young Lady Ximen! When is the Third Round of the Tournament coming, um? You have a company it seems. Who is this? Huh? Oh, a son? Ah. Yes. It's nice to meet you."

"Lady Heavenly Flower Unni! Changa drew on the bricks, ah! Ah. Who is this older brother? Eek. A son…….? Hehe. I am Jin Yuwol."

"Wow, Qing'ah? Who is this handsome young man you brought? Oh, that's right. I see. Oh, a pseudo-adopted son is very handsome. And wow, his manners are impeccable too."

The people of the Jin Clan who were off-duty greeted Qing with delight.

Even though he acted strangely with his own mother, refusing to use formal or even informal speech, he was extremely courteous and respectful to others, which was quite infuriating.

And finally, a ray of light descended.

"Young Lady Ximen? What in the world is going on here? No, can that even be considered logical? Calling someone your adopted son when you barely even became a maiden? If you have any sense, you shouldn't act like that."

"Lady Jin!"

Qing quickly grasped Jin Seol's hand.

Wasn't this the reaction of a normal person?

However, Jin Seol was cold.

"Young Lady Ximen, you're the same, you know? I know that Young Lady Ximen is a good person, but how could you accept it just like that?"

"That's right. That's totally right."

Regardless, Qing was moved by the exchange.

She wanted to share this emotional moment with them, but since the Jin Clan members were all busy people due to a shortage of personnel, they had already taken off for business inspections.

Qing herself also had things to do, so she couldn't just keep wandering around the construction site at Guang Zhou. It was time to start properly requesting construction.

As such, Qing was dressed as a Construction Fairy and started searching for a lumber mill, and naturally, there were quite a few people who recognized the Fairy.

"Oh, Fairy. You finally accepted it, I see? Yes, all those deeds must be for merit."

"Where are you having construction today? Ah, you're giving out construction work today. Are you the one in charge of the master carpenters, Fairy? Ah, you aren't. You're entrusting it to the Gangs or Yangs. Oh, but you did finally end up with him, I see?"

Even the bratty little girl from yesterday, somehow knowing what was happening, came running up and started acting coy with her arm around Qing.

"Aht, Mother!"

"Hey, how do you always show up like this, little girl? You're already chasing after men like that? You can't do that!"

"Hehe, Mother, why don't you just think of me as your daughter for once?"

"I'm not interested in the romance of you guys, so just resolve it amongst yourselves."

"Hey. I already told you, I'm not into kids. Did you think a kid would want someone my age?"

"I'm not a kid! I'm fifteen this year! I'm an adult!"

"Little girl, I'm fifty. If you've lived about three times more than her, she's pretty much a child to me."

"……? That's a lie. I'm not getting tricked."

Since the story from yesterday had already spread throughout the city, those who saw Yeom Hwiyoung smiling brightly behind Qing all thought it was a good match.

"Fairy, oh my, may I ask to be a master carpenter? I'm quite skilled when it comes to construction in Guang Dong, but if I take that spot from you, Fairy, there will be a lot of murmuring behind my back. So, if I may ask, would the adopted son become a carpenter or a successor to the Shamanic Temple?"

Qing was now a recognized Master Carpenter, rather than just some rookie carpenter.

When she first proclaimed herself as the Construction Fairy, she had merely been a rookie carpenter masquerading as one, but now, there wasn't a single master carpenter in Guangzhou who doubted Qing's skills.

Now, she was an experienced carpenter who wouldn't seem out of place even when leading a construction project as the master.

So, from the master carpenter, there was now a steady dialogue of highly-skilled exchanges. With discussions over how many people were needed, how the construction should be done, what kind of materials there were, how much material should be procured, and how they should be used.

Yeom Hwiyoung, while sitting on a stump that was commonly found along the lumber mill street, watched it all with his chin propped up on his knee.

The corners of the son-pretender's mouth curved gently.

The daughter of a vegetable store gazed at him, then at Qing, and then back at Yeom Hwiyoung. After doing this about three times, she started shaking her eyes in disbelief.

"Big Brother? No way? Right?"

"You little thing. Mother was right to say that you were already a bit too far gone, huh? Already acting all indecent. It seems your nature is just as rotten too."

"Ah, it's not that. I was just…"

At this, Yeom Hwiyoung tousled the little girl's hair.

If Ximen Surin saw this, she would have scolded him for messing with the hair of a woman, as if it was their lifeblood, even if she was a mere child.

After following them for just half a day, anyone he met greeted him with great enthusiasm as if he was a local who had lived in Guangzhou since birth.

Though he was a great elder of a righteous Daoist Sect, and even a Master of the Transcendent Realm, and a fearful being to the commoners, no one seemed to fear him at all.

"She says she's a comfortable person, huh? Maybe she's just an idiot. Still, it doesn't seem that bad."

"Hing. I made sure to have my hair done today…. Um, Big Brother, what did you just say?"

"It's nothing you need to know about, you lewd child."

"Hing, are you going to keep doing this?"

"I'll keep doing this, alright? So what can you do?"

Yeom Hwiyoung asked after teasing her, suddenly recalling something.

"Oh yeah, about those loan shark bastards. Are they still okay? Did they not bother you anymore?"