\chapter{When Mom Goes to the Island's Shade to Pick a Head (3)}

Qing never stopped those who came to her, nor did she hold back those who wished to leave.

Even when Choi Leeong, in his dementia, had thought of Qing as his daughter, wasn't she still resolute in her stance that while she was fine with calling him "Gramps" but she was not going to act as a replacement for his dead daughter?

Thus, a wannabe son who wanted to make her his mother was actually safer compared to Choi Leeong.

At least the Supreme Lord was looking at Qing for who she was when calling her ‘Mom' instead of trying to use her as a replacement.

Of course, the visceral revulsion was something she couldn't help.

If it wasn't a wannabe son but a wannabe daughter, she might not have felt such great revulsion.

You could say that they are both her children, but the feeling of having a son and a daughter was completely different.

Ah, shit. If only I wasn't at the Transcendent Realm, I would have had a decisive battle with him using nukes or some other form of violence, rejecting him through sheer force.

So they say that national power lies in its military strength.

Since I'm weak, I'm being forced into adopting him. What is my fate……

Anyway, he asked me to give him a name.

Thankfully, he already had a family name.

The Divine Vein of the Heavenly Demon Divine Cult used the surname Yeom(炎) generation after generation. It seemed that the spiritual parasite who took on the Heavenly Demon's vessel within me was also a Yeom.

But how should I come up with a name?

Are there people in Zhongyuan who get paid just to come up with names?

But, it's somewhat irrational to get paid for coming up with a name, isn't it?

If you're given the authority to name someone, shouldn't you be the one paying?

Perhaps because she wasn't killing a bad guy right now, Qing's thoughts were running wild and free.

It was Qing in her natural state.

As she was thinking to herself, another prodding demand came her way.

"Mother, when will my name be revealed?"

"Can you wait patiently for a little bit? I can't just give you a name haphazardly. You might become a Gabdol or Gabsun."

"I don't mind if you make up my name haphazardly? Whatever name Mother gives me, I will be fine with it."

"Really? Then, how about Byeonghal2?"

"Byeonghal? What does it mean?"

"Since your surname is Yeom, it's Yeom Byeonghal."

"……How much longer do I have to wait?"

It seemed that ‘haphazardly' or ‘whatever' didn't include ‘Yeom Byeonghal'.

Qing snorted with laughter and replied.

"Alright, could you stop asking me every three-quarters of an hour?"

For reference, a quarter of an hour was fifteen minutes in Qing's old world, so asking her three times every quarter of an hour meant he was asking her every five minutes, practically singing ‘what's my name, what's my name, please call my name'.

"Wait patiently for just a few days."

"I've waited fifty years for the day I would receive my name. Asking me to wait even longer is too cruel. Is it not?"

"Hah, if you waited fifty years, you could probably wait a bit longer too."

"……? Mom? Is that really the way to look at it?"

"Ugh. Didn't I say not to call me Mom?"

"To think you won't even allow me to call Mom, ‘Mom'. How can there be such a heartless thing in this world? Is this truly alright? Mother?"

"Yeah, I'm disqualified as a mom, you son of a bitch. Why don't you go find a mom who'll let you call her mom?"

"Everyone has shortcomings. Even if my mother is a bit heartless and severely weak, what can I do if she's still my mother? It seems that I, who is at the Transcendent Realm, have to endure."

"Ugh."

Qing swallowed her grief.

To think she, a peak-Transcendent Beyond Transcendent Qing-nim, had to be told that she was weak.

And by a moron who just went ‘blah blah blah' until she sold his eyeballs!

There had never been such an insult in the world!

I'll have to reach the Unrestrained Realm, no matter what, seriously.

But how do I get to the Unrestrained Realm…?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After being cared for by the Divine Physician after a long while, it was so comforting and wonderful.

She didn't have to lift a finger and yet, she would arrive at the bath, her clothes would come off automatically, and the fragrance of the soap would envelop her entire body.

The feeling of her entire body being carefully covered with soap was so comfortable, and well, it was also a little erotic and tickling. Something very nice, but hard to describe……

And after that, when she plopped into the bath, there was no paradise that was better than this.

"Is the temperature okay? Shall I add more fire?"

"No. It's just right. Hmm."

Then she noticed the number that kept appearing above the Sister in law's head.

She had forgotten about it because she was too dazed at the mention of "Mom".

Qing's eyes wandered without finding any particular target.

Nah. What's the point of worrying about those numbers?

I should just look at the Sister's chest.

Hehe. The chest is massive. It must be really heavy. Then again, it is heavy. After all, didn't a study done in my home country say that looking at a chest increases life span? So I should look at her chest. I should look at her chest and live a long and healthy life.

It was when Qing was swallowing down her usual lewdness after a long while.

"Sister? What's wrong? Do you want to touch my chest?"

"H-Huh. Suddenly coming at me like that…"

"No, I noticed you were staring intently at it."

"W-Well, if you would be fine with it, then I, this unworthy one, will touch it just a bit……."

"Yeah. Here."

Gyeon Pohui leaned forward, resting her chest over the edge of the bath.

As such, the large, fatty mass above her chest came right in front.

It was a generous and excessive consideration, to let her caress it comfortably.

"Gasp."

Qing unknowingly let out a breath.

Gulp. She swallowed.

The effect of the chest was tremendous!

The uneasiness towards Righteous Karma and Evil Karma that had been pricking at one corner of her heart vanished completely under that soft sensation.

"Kyaa! Sister, it tickles!"

Gyeon Pohui's giggling rang out clearly in the bath, where a thick steam rose into the air.

However, in place of the Righteous Karma and Evil Karma counts that she disliked seeing, impure killing intent subtly spiked, and started to spread as if a single drop of ominous paint had been dropped in Qing's pupils.

That's right. I wanted to ask the Sister something when we meet.

"Ah. Sister. You know."

"Yeah?"

"The Sister's martial arts, when she does ‘that', does the other person also feel good, or something like that? What kind of technique is that? Or is it some sort of martial art?"

"Umm, rather than feeling good, it's closer to forcefully holding them in place. When pleasure reaches its peak, everyone can enter a state of trance, right? Ah, trance is a state where ‘I' is absent-"

"I'm a Daoist, you know? I know what trance is. Isn't that why there's yin and yang exchange in primitive Daoism? It's a moment where you abandon yourself, even if it's just for a moment, and come into harmony with nature."

"Yeah yeah! Sister is so smart! If you enter a trance, for that instant, the origin will also be without an owner and defenseless, so that's when the origin is extracted. Ah, the origin is similar to Innate True Qi."

"I said I'm a Daoist, you know? I know what an Origin is. Get rid of the unnecessary details."

The Origin was the core of the Innate True Qi, and if it was compared to the body, it was a role akin to the heart of a meridian.

Just as the heart circulated blood through the body, the Origin was also the core of the meridians that held a person's True Qi.

Because the Origin was located in the Dantian, Innate True Qi also resided there, and also used the origin's property of holding onto Qi, various Inner Qi Cultivation Techniques used breathing methods to capture the Qi of nature and form a Dantian.

So if an Origin was extracted, then the Qi of the Dantian, including Innate True Qi, would be completely ripped out.

And when one's Innate True Qi was lost? Obviously, they die.

To calmly talk about extracting an Origin, it once again made me think that the Divine Physician was not quite right in the head.

Did she not know the difference between good and bad? Or is she just pure?

I can't tell if she doesn't know the difference or if she is choosing not to know.

"So at Bliss Palace, they stimulate one to reach a trance as quickly and deeply as possible."

"Yeah. That's right. That's what I was saying, it's a martial art, right? Can you tell me the formula and details?"

"I can tell you, but there are some side effects, you know? Is that still okay?"

"Side effects? What are they?"

"Your senses will become dulled. I guess it's because you can't enter a trance before your partner, but, ah, since you have also mastered a secret technique, it wouldn't matter, right?"

"Really? Even better. Let's do it now."

"Yeah! Should I call them right now?"

It was an instant answer without any hesitation.

At that, Qing made a ferocious smile.

She'll take a shower and then, she'll be back, she said.

Qing laid on the bed, spreading out her hair.

With hair this long, it would take forever to dry.

While doing this, Qing opened the Martial Arts Window.

Ecstasy Like a Fairytale. Red Border.

Since she had heard the complete formula, it was in a state of being temporarily registered.

As she tried to invest Practice Points to master it, a disgusting sense of her brain being kneaded, a feeling she hadn't experienced in a while, made her pause.

Ugh. It has been a while since I tried brain kneading, and my mood is absolutely awful.

Qing took a deep breath and braced her heart, until, suddenly, a question came to mind.

It's nicely called Yin-Yang Exchange Technique.

Commonly known as the bedroom arts, it's a lewd art used to extract the Origin.

But why am I trying to learn this?

Ah, she said my senses would be dulled.

Regardless, thanks to this, as she opened the Martial Arts Window again after a long while, the Blissful Maiden Arts had reached Ten Stars and the bar was almost at its very end.

The timing was just right.

When it reached Twelve Stars, the Grand Star, the weight of the martial art's effects would be immense.

Since the Blissful Maiden Arts was something that automatically grew due to automatic training, if she had been unaware and it reached Grand Star, it might have caused a terrible accident during combat.

Thus, Ecstasy Like a Fairytale. Cost-effectiveness at Six Stars.

And, after a long while, the familiar feeling of her brain twisting and turning.

Qing, writhing on the bed with her eyes rolled back in her head, suddenly regained her focus.

The Martial Arts Window was still floating in the air.

Perhaps thanks to making a killing from the Green Woods, or perhaps from dealing with many of the small missions that appeared randomly when she was out of it, her Practice Points had accumulated quite a bit.

Should I try to reach Grand Star on one martial art?

But since I might go crazy again, I'll put off the Great Righteousness Heavenly Heart Technique and Yijin Cleansing Method and Dragon Form Vajra Heart Technique for now.

Ah. The Wheel of Demonic Calamity. This is the real deal.

After checking the Practice Points, Qing poured them all into the Wheel of Demonic Calamity and reached Twelve Stars, the Grand Star, in an instant.

Then, her muscles all over her body itched, her eyes itched, her nose stung, and her ears made soft, subtly grating noises.

But what's new, it's just something she had experienced before.

When her physical stats increased, she didn't suddenly become stronger or have better eyesight.

It was a feeling of her body slowly and gradually strengthening while feeling like she was being tickled all the time.

Ah. Dangerous thoughts. Other thoughts. Good thoughts.

Qing was surprised and quickly switched her thinking.

Usually, if she thought of something that didn't feel quite human, a panic attack would usually come over her.

But it was already too late.

Once a thought had already surfaced, she couldn't stop it even if she tried to consciously change the course.

What kind of person's body is this that becomes a superhuman with senses, strength, stamina, flexibility, and more?

Is this body even human to begin with?

Then, a face suddenly came to mind.

The gaze of the Empress, brimming with love, so much so that it was hard to even meet her eyes.

Come to think of it, isn't my body the body of the Princess of Yeon?

Then, it must be human, right?

Then, she felt surprisingly calm.

It's just that I'm beyond human in many ways, but in the end, my very root is still that of a human, right?

And then she unknowingly let out a laugh.

Why was I so anxious about something so simple?

As she was relaxing with that relieved heart, Gyeon Pohui, with wet hair, entered the bedroom.

She immediately approached the bed, carefully moving some hair away, and then laid down on it.

Qing chided her.

"What are you doing? You're going to sleep without drying your hair?"

"No? Didn't you say you wanted me to try out a new martial art? You also said you wanted to practice it with a real person to become skilled at it. You wanted to know how it feels to discover a weakness and cringe?"

Come to think of it, she did say something like that.

Why did I do that?

Qing waved her hand.

"Pfft, we shouldn't do that to each other when we're family. Ha, it's just a joke, it's a joke."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing slept very well last night.

For some reason, being hugged by the Sister in law felt different compared to sleeping with her other friends, It was a very comfortable feeling.

That was natural, since unlike Qing's friends who were flustered and nervous by her side, the Sister just cared for her comfort, so her stance was different from the start.

But as if she, who always fell asleep before anyone else, would know about that.

She only thought that the Sister was always good at propping her up.

Qing, having woken up with such a clear mind, left the bedroom, only to see this.

A punk was kneeling on a mat in the courtyard.

"Mother, did you sleep well?"

"Ah. So, that wasn't a dream. Someone suddenly said I was his mother, so I thought it was just some crazy dream."

"Isn't it customary for children to greet their parents in the morning and in the evening? You should be happy to see your son's face from the morning, right?"

"Is that what's considered a morning greeting? Is waiting for you while kneeling on a mat how it's supposed to be? It's more like an official apology or something. Are we holding a funeral?"

Even when she spoke so coldly, he just smiled foolishly as if he liked it.

Qing let out a deep sigh and said.

"I've decided on a name."
