\chapter{When Mom Goes to the Island's Shade to Pick a Head (8)}

The Changryong Trading Company was always receiving precious items from beyond the borders, no matter where they were.

Since no one had ever seen them embark on a proper merchant voyage, it was a truly mysterious thing.

Officially, it was because they engaged in a secret and mysterious trade journey.

However, there was no one in Guangzhou who didn't know that this secret was that they were actually engaging in smuggling across the sea, ignoring the national laws.

Of course, Qing had never been so loyal to her country that she would foam at the mouth and shout ‘Execute them!' just because someone had broken a national law that even dogs didn't obey (although the opinions of dogs should be heard).

However, she could not forgive the fact that the manpower for rowing, the main selling point, were slaves who were unwilling, free workers who were forced to work with passion.

They used the slaves they would sell as manpower to cross the sea.

And if a slave died along the way, that would be the day meat dishes were served.

They were the very embodiment of innovative efficiency— slaves as products, manpower, labor force, and food— surpassing even the Western Cozeners.

Or perhaps, they were going against the times by specializing instead of separating labor.

"Great Expert, I am fine. So please, just save my children! I beg you……!"

"Father! No, it's me. I, I will pay for my sin instead."

"No. Great Expert, please forgive us with my life, as all of this is my fault for being without virtue!"

It was truly a heartwarming scene— one that could never be expected from an Unorthodox Faction, seeing a family competing to sacrifice themselves to die instead of the other.

At that, Qing was smiling brightly, though it wasn't visible under the veil.

"Wow, just look at how this old man speaks. Hey, did anyone say we're going to kill you? Uh-meh, did you hear what this old man is saying? Does he think we are some kind of evil and bloodthirsty demon?"

"Yeah. That's too much. Although Uh-meh likes killing people, she's a very nice bloodthirsty demon, you know."

"I'm so sad. But Mister, you know your family is precious, but why did you steal and sell other people's families? My family is family but other people's families are livestock?"

"A death sentence, please……!"

"Well, I'll let you live. Oh, Uh-meh, do you know that story? About the blind man and the cripple helping each other on a journey. The cripple carries the blind man, and the blind man guides the way… Oh no, it's the opposite. Anyway."

"I don't know! It's my first time hearing it!"

"You see, it's like they're filling each other's gaps. With such deep family bonds, wouldn't they be able to make it work if I leave one arm and one leg each?"

Thus, the family members had their joints in their arms and legs broken, and were sprawled out nicely.

Since one arm and one leg each were left intact, there were four left arms (one had a left hand), and five left legs among the ten family members.

Anyway, when Qing got up from her seat without touching them any further, the family members with their broken limbs showed a sign of relief despite being in pain.

Until she opened the main gate and saw the items— a combination of products, manpower, labor force, and food— that were gathered in the courtyard.

"Well then, everyone, have a fun time."

As Qing waved her hand, Uh-meh also waved her hand along with it.

At that, the products, who couldn't even lie down in the narrow storage and had been stored in close proximity to one another, stepped out with dirty feet into the main hall.

Qing went through the main gate and put the signboard back in place.

The signboard of the blood-soaked Changryong Trading Company was hanging askew at the very edge.

Unlike the Changryong Trading Company, which openly smuggled, the Ohga Shipbuilding Company was a wonderful organization with a thorough spirit of abiding by the law.

According to the national laws, making illegal ships without the permission of the government was strictly prohibited and was punishable by death.

As such, the Ohga Shipbuilding Company took the lead in punishing vicious lawbreakers who dared to secretly assemble ships.

Of course, the national laws stated that commoners should not kill other commoners under any circumstances.

Therefore, the Ohga Shipbuilding Company, with its thorough spirit of abiding by the law, did not break the law. They simply beat them up and showed the wretched appearance of criminals to the entire city before handing them over to fellow smugglers in Guangzhou and receiving a small compensation fee.

They were definitely not selling them.

Since the sale of slaves was prohibited by the national laws, they were not selling them, but merely receiving a small fee, a small reward for upholding the laws.

With such a wonderful, exemplary workhouse, how could the government not treat them favorably?

Therefore, as soon as they took down the signboard and went inside, the government soldiers with large ‘government' characters stamped on their uniforms, aimed their thin, trident-like spears at Qing all at once.

"Stop! The national laws are inviolable, yet you dare to cause chaos in broad daylight!"

Qing stopped and looked at the faces of the high-ranking officials while loudly muttering to herself.

"What to do. I need to kill them all to get away without being caught. If I miss even one, things will get troublesome."

"Hmm. Then should I block the gate?"

"Nah. Would they even know our faces? Or even our names? What does it matter if we miss one or two? Just quit being a shaman and leave."

"Wow, that's right. Uh-meh always has a plan."

At the blatant threat, the government official's face lost a bit of color.

Whether that was the case or not, Qing pretended as if no one had heard her mutter and brazenly stepped forward.

"Look here, Honorable Sir, who are you to block the path of this shaman?"

At that, one of the lackeys, who took it upon himself to take offense, shouted.

"This is the Deputy Inspector of Guangzhou's Regional Surveillance Office! You will kneel and show your respects right now!?"

"Ah. Deputy Sir. But does my face not seem familiar to you? I'm the Earth Shaman. This house is filled with evil spirits, so I came to exorcise it, but how can anyone living in a house filled with evil spirits put their feet in here?"

The Deputy made an effort to sound dignified.

"Ahem. Confucius said that we must avoid mysterious powers and chaos. Stop speaking with that bewitching tongue of yours and immediately turn around and leave."

"Tsk. That's a fool who cannot even discern between heaven and earth. You might be stricken with a curse if you side with a house touched by a great evil spirit. You should know that. You know that, right?"

The great evil spirit was saying so, clicking her tongue.

And then continued to say,

"It's a terrible curse where people die in a horrible way in the middle of the night. Let's see, I should try reading my own name by the heavens. I'm not cheap, you know. What's your name, Deputy Sir, and where do you live? And do you perhaps have a particularly precious child? A precious child that you'd regret losing for the rest of your life, if they die?"

The official interpreted this as follows.

Where do you live?

Should I kill you or your children?

And in fact, since Qing had said it that way, he heard it quite accurately.

"I tried to drive out the evil spirits, but the Deputy has stopped me, so even if a series of funerals occur in your house, it is none of my doing. I warned you, so do not regret it later. Go ahead and have a proper ritual at the Confucian temple so that the late Master Confucius can protect you from such mysterious powers and chaos."

With that said, Qing turned her body around.

"Uh-meh, do you perhaps know where the Deputy lives?"

"Nope."

"Whatever, then. I can just ask anyone in Guangzhou and they should know. I should write out a Sutra for them so that they can prepare for a major funeral."

Oops. The Deputy grabbed onto Qing's clothes.

"Ahem, that…. You said you were here to exorcise evil spirits."

"Ah. So it's starting to feel chilly, huh? I guess you can feel the chill of the evil spirits now?"

Qing snorted and looked back.

"Originally, ghosts don't care about the government or Wulin. Unlike the government and Murim who pretend that nothing's happening, they just cause disasters when they are out of line. Do you understand my meaning, Deputy Sir?"

Don't you know about the inviolability of the government?

Just butt out and leave, okay?

"Confucius said that a nobleman should avoid mysterious powers and chaos, but he also said to protect innocent civilians from being tormented by mysterious events. I don't know much about shamanism, but if it brings relief to the common people, then isn't it a good thing? So please, take care of it yourself."

I understand. I'll leave you be. Please take my circumstances into consideration.

"Deputy Sir is quite clearheaded, hm? I will try my best to prevent harm from reaching your home. Aren't you thankful?"

I'll let you off the hook. Don't interfere.

"Ahem. I am thankful."

Alright, I get it. Thank you.

"Alright, let's go!"

The Deputy dismissed the government soldiers with a disgusted look on his face and walked away.

It could be said he was running away quite shamefully, but…

My seniors always say that it's better to not engage with crazy people, especially crazy women.

One had to at least pretend to fear the government to get away with a threat.

And if one rushed to fight while saying ‘let's die together,' the one who always sheds blood was the government official.

The inviolability of the government was always just an excuse for government officials.

"Your Excellency! If you go like this! Your Excellency! Your Excellency!"

The lackey wasn't from the government.

He tugged on the edge of the Surveillance Department's official's clothing, but with a ‘Just let it go!' he was shrugged off — No, he didn't fall down, because if he had actually learned any martial arts, he wouldn't have fallen at the mere gesture of a bookworm reading the classics.

And so, as the lackey shouted ‘Stop it, it's not right, stop it! You can't do this after receiving such sincerity,' the Deputy, who just wanted to get away from this miserable place, finally burst into anger.

"You outrageous bastard! Who do you think you are to slander someone! Come here, why don't you, and become a traitor before the evil spirits do!"

Only then did the lackey finally let go, and with that, the government soldiers had all left, leaving the courtyard empty with a depressing, slumped silence.

Then suddenly, he looked at Qing and gave a sly smile.

"Hehe, Fairy. I have heard the rumors of your spiritual power, and I have always admired you. If you need to ask me anything, please do ask anything, hehe……"

It seemed they weren't so law-abiding after all.

They were experts at secretly making holes in boats at night and sinking them if they belonged to commoners.

And if repairs for a boat came in, they would endlessly delay the process and steal the ship.

Since no ships came in, they had actually started bribing the authorities to seize ships, feigning as if they were inspecting them.

They were either boatwrights or ship-stealing bastards with incredible skill.

At this, Qing shook her head and said.

"Uh-meh, close the gate and bolt it shut."

That was how the gates of the Ohga Shipbuilding Company were firmly shut.

At the Abode of the Vanguard, Clean and Auspicious.

The Abode of the Vanguard was the base where ship captains and crews of large ships usually resided.

And according to an anonymous informant, whom she didn't ask the name of before killing, and who divulged information for public interest before dying, the Clean and Auspicious was a pirate ship.

Mountain bandits were all trash, and they all deserved to die.

Pirates were also all trash. They all deserved to die.

The pirates didn't set up some grand manor and seemed to have converted an inn, so the guest rooms were used as their own private rooms, and the first floor was… ugh, what a smell.

Qing entered the Abode of the Vanguard by kicking open the gates and immediately frowned.

The smell of opium, cannabis, and tobacco all mixed together to create a fog that filled the room.

On top of that putrid odor was the sour smell of cheap alcohol mixed with the stench of men, making even Qing, who had a strong stomach, want to puke as a fit of nausea rose from her throat.

The bustling chatter in the hall was silenced in an instant as the veiled woman suddenly appeared.

Just as someone was about to speak, Qing took the lead and held up the hammerhead.

"Alright, everyone, pay attention. Sparkle sparkle. Well, I'm just gonna do my thing and leave, so keep your eyes down, you bastards."

The pirates lowered their eyes at the sight of the shining Sword Force.

"Sparkle, sparkle."

From behind, Uh-meh added with a cute interjection.

Qing chuckled.

Her face was that of the most alluring seductress under the heavens, with the sex appeal flowing out of her. And yet, she still acted cute.

Of course, she was not cute to the pirates.

After all, they couldn't possibly think that a master, who could unleash Sword Force with just her bare hands, was cute.

However, Qing was still unaware of Uh-meh's realm, so she didn't know that Uh-meh was actually emitting Sword Force, not just metaphorically.

Qing's veiled figure scanned the room.

The pirates, unable to understand the situation, were just thinking ‘Someone must have bothered someone important. They came all the way here to fuck us up. So, let's just stay still and not die with them. Let's just stay still. Yeah, let's just stay very, very still.' as they lowered their gazes.

But Qing wasn't looking for someone.

Qing finally found her target and cut through the hazy room with only the sound of her skirt rustling.

Then, there was the sound of the hammer head being raised, a heavy swooshing sound of the iron tool flying through the air, and then bang! The sound of something cracking.

A pillar exploded, sending bits of wood everywhere.

And then, Qing slid forward again.

Whoosh! Bang! Crack.

Then, Qing headed toward the entrance, destroyed the pillar near the entrance, and leaned the hammer on her shoulder, saying:

"Hoo. All done. Let's go."

"Uh? Already? Without killing them?"

"Ugh, it stinks. I can't stay here any longer. Let's go."

Qing linked her arm with the Uh-meh, who was tilting her head with a bewildered look, and headed outside.

As the two stepped outside, the sound of wood twisting and groaning eerily rang out as if lamenting being left behind.

Soon, there was a cracking sound as the wood split.

The ground was fine, but the Abode building started shaking as if there was an earthquake.

Qing was a carpenter. If she saw the inside, she could roughly grasp what load each beam was carrying.

She knew which pillar to destroy to make the building collapse.

"O-Ooooooh……!"

The pirates, finally understanding what had happened, rushed out in a panic. However, the one who had been leading the charge flew back in a trajectory as if he was thrown, causing the rest to collapse into a huge pile.

In the eyes of the pirates who fell, they saw the ceiling shaking and distorting amidst the dust.

And then… CRASH!

The sound of several thunderbolts rang out grandiosely near them. 