\chapter{When Mom Goes to the Island's Shade to Pick a Head (7)}

Usually, when referring to shipyards, it meant a collection of ship builders (ship construction), lenders of large ships, merchants who wrote it as private trade but read it as smuggling, and those maritime thugs who openly showed off the results of their pirate raids.

The Grand Sea Palace Shipyard was the most famous of the large shipyards in Guangzhou.

Amidst the two doorkeepers who were foaming at the mouth and twitching on the ground, Qing looked up at the signboard of the Grand Sea Palace Shipyard.

The signboard was the face and pride of the organization.

The executives of the Guangzhou shipyards were partners and rivals, so they were subtly engaged in a battle of pride, akin to a group of wealthy individuals.

One result of this battle was the magnificent signboards, fit for a palace.

They would invite a famous calligrapher to write the text and use the highest grade red sandalwood to build the frame, creating a sturdy precious relic that could be passed down through generations.

For this reason, disaster had fallen upon the warriors of the Grand Sea Palace Shipyard.

Thud! A sword became embedded in the signboard.

A sword embedded in wood was usually difficult to remove, so before they could even react, Qing forcefully pushed the four characters of the Grand Sea Palace Shipyard forward with great strength.

As if a gigantic wall had come crashing down, multiple warriors fell at once.

And above them, a hammer head came crashing down, smashing down upon one hip bone.

Crush.

Half of the pelvic bone completely shattered.

At most, he had a few months to live.

If he was lucky enough to survive, he would have to live the rest of his life with a crooked hip that sagged downwards.

Perhaps sensing his fate, a spine-chilling, desperate scream erupted.

Regardless.

The hammer head sprung back up.

Then paused.

For, from between the legs of the warrior who was desperately flailing and retreating, a dark stain was rapidly spreading outwards.

A clear expression of contempt appeared on Qing's face.

The hammer smashed the shoulder of another warrior, and instead, the straight edge of the signboard dug deeply into the ground, like a fortress wall.

Two calves, free from the oppression of the knee.

The severed limbs enjoyed the freedom that they were met with as they tumbled along the ground.

"Net, throw the nets!"

Qing flinched, and then, seeing the warriors rushing towards her with their arms full of nets, she was at a loss for words, clicking her tongue.

What a joke. What good would it do to try and throw fishing nets on the ground?

They couldn't even get close to Qing, and just helplessly covered the ground, tangling with the warriors who were already groaning in pain and only intensifying their suffering.

They're trying to charge at the intruder, just to end up rolling on the ground.

At this moment, their fear of the mysterious Earthwork Divine Maiden and her attendant-like expert grew stronger than their grief and rage over losing their comrades.

The moment when fear overpowers bravery is also the moment people start to run.

Amidst the chaos of people fleeing for their lives, the warrior who was supposed to be the captain of the guards still maintained a sense of duty.

"I will stop them! Flee!"

His spirit was admirable.

The guard captain flew through the air after just one exchange of blows.

As he was told to run, the Grand Sea Palace Shipyard owner, without the slightest hesitation, flew up into the air and crashed into the captain's back, both tumbling down in a disheveled mess.

It was truly heartbreaking loyalty.

Even while all tangled up, the owner was actually protecting him with his body, what a sight.

Qing nonchalantly kicked the protective cover away.

The guard captain, who was kicked in the belly, shuddered and kept vomiting blood, but the owner seemed to care more about his own safety.

"Wait! Spare, spare me!"

"Hmm."

Then, a man who had been trying to make a run for it when the owner had fallen was dragged over, held by his head by Gyeon Poye.

A moment later.

The owner and general manager were now kneeling down side by side, rolling their eyes as they read Qing's expression.

Even if they checked, they probably couldn't see her eyes which were covered by a veil. However, if someone wanted to live, shouldn't they at least try?

Qing stood askew, looking down at them.

More accurately, she was looking at their Evil Karma.

It was enough Evil Karma for her to kill them without hesitation.

"Someone must die here."

The shoulders of the two men visibly jerked at Qing's sudden words.

"Owner? Is there any reason I should spare you? Convince me."

"That is-"

The owner desperately opened his mouth.

However, thud, thud, thud. The hammer struck the ground, cutting off the owner's words.

"General Manager? You have to explain why the owner must die. Convince me that I should kill the owner. Why? Because one of you two must die. Do you understand what I mean?"

"Y-Yes, I do!"

"Good. Then start. Shall we start with the owner? Why should you live?"

"If I, I am gone, the fishermen of Guangzhou will immediately starve. I own one out of three ships in Guangzhou…"

"That is not true! If that bastard dies, won't all those boats be left without an owner? Instead, it is because of that piece of trash that the fishermen of Guangzhou are poor!"

The price of renting boats wasn't cheap.

Also, using a term from Qing's world, instead of a set price, the price was structured such that once they paid a deposit, they had to pay a final payment based on their catch.

So, the fishermen were always barely surviving.

After all, wasn't their job to catch fish?

If they were hungry, they could just eat fish.

This was the typical Zhongyuan way of kicking the ladder away after climbing it.

The fishermen's dream was to save up a bit of money and someday own their own boat. However, from the standpoint of the one who had to lend the boats, how could he survive and run his business like that?

So, even if they filled their boat to the brim with fish, they would only get a few coins in their hand.

And so, the boat owners, who had a massive income, would use that money to hire thugs to beat up any rebellious fishermen.

After all, it was more pleasing to them to give money to human scum and have them beat up people than to give money to the fishermen themselves.

"Hmm. I want to beat you to death, but can I really say that merchants seeking profit is something that deserves to be killed?"

At that, the ship owner's expression visibly lightened.

At that, the general manager shouted desperately.

"It's not only that! He purposely causes flaws in the boats to extort compensation and burns down ships that should be decommissioned, and makes them pay by selling their children!"

"You, you bastard!"

"He's not the only one who did it! Who do you think gathered thugs and gave them money?!"

"I-I had no choice, you know!? They would have killed me too and dumped my body in the ocean if I didn't!?"

While facing the person who had their life by the neck, the two were fighting each other, saying the other one was the bad guy.

Whenever the general manager exposed the owner's evil deeds, the owner would also become enraged and start shouting.

‘Who do you think ordered you to do that?! Did you think I wouldn't know about you stealing gold and silver in the middle to line your own pockets?! I was just letting it slide since you were my general manager, but you repaid my kindness with treachery!'

As such, wicked deeds that no one particularly asked for began to pile up one by one.

It seemed that there were still some conscientious ship owners when the Jin clan was still around.

However, as soon as the Guangzhou Shipyard began to officially flex its muscles, a series of mysterious attacks and accidents occurred, resulting in many deaths.

And here, one of those culprits was firmly rooted in his place.

"I don't understand it. Why are the bad guys always truly bad? If it's like that, then I have to kill you."

Without fail, those who are good, are good and those who are bad, are bad.

Especially those bastards who called themselves the Unorthodox Faction. They were never right.

Was it that those bastards became evil because they were part of the Unorthodox Faction, or that they were that evil from the start?

Qing lifted the signboard.

At that, the owner kneeled down and begged.

"P-Please spare me! If you spare me, I will truly live kindly from now on!"

Qing's movement came to a screeching halt.

Like a person who had forgotten how to breathe, she stopped still, without a single twitch, just like the Four Heavenly Kings in front of a Buddhist temple.

It might not be true, but what if it was?

What if they repented now and lived as righteous individuals from now on?

It was then.

"DIE!"

The general manager pulled out a dagger from his bosom and lunged forward.

Thud. The sound of flesh being pierced wasn't something heard by the ears, but seen by the eyes.

The ship owner looked down at the dagger piercing his belly with trembling eyes.

"Y-You……!"

"Hehe!"

The general manager tried to pull out the dagger, but the owner's will to live firmly held his hand in place.

At that, the general manager swung his fist.

He straddled his body, using both fists to pummel the owner's face.

Whack, whack. The fists pounded as if to break, with groaning and gasping, the general manager yelled.

"Die! Just die!"

Then at one point, the general manager's Evil Karma dropped by four points, and the number of 300 changed to 298. All the numbers changed at once.

It was a dramatic change.

For some reason, pop, she unexpectedly burst into laughter.

It wasn't just a little chuckle. She burst out laughing.

She burst out laughing all by herself.

She laughed so hard.

Ah! It was so funny that she couldn't even breathe! My gosh, where is such a masterpiece from? Was it perhaps a family heirloom? I'm truly laughing so hard, I can't breathe. Are you perhaps the Great Master of Jests from Zhongyuan? You must be the King of Jokes! Please, compensate for my missing belly button! I can't breathe, this is a murder-joke! Please, spare my life!

Qing's steel-like abs ached so much and tears welled up in her eyes, blurring her vision.

Her clear laughter, kyahahahat, drowned out the moans of the warriors, filling the world with its volume.

The general manager was terrified, flailing around and trying to back away.

Then, when his back reached the wall, he started trembling, unable to hide his fearful gaze.

"Haaa. Yeah, that was pretty impressive, khuk, khuk."

She almost wasn't laughing but sobbing, her laughter continuing with lingering aftereffects.

At that, Gyeon Pohee could no longer hide her worried expression.

"Um-mae? Are you okay?"

"Yeah. I somehow, feel refreshed."

If it's a bad guy, she should just kill him, what was the point in even thinking about it?

In Qing's eyes, a sinister color spiraled out with a long tail and scattered like fireworks illuminating the night sky, covering her entire eyes with a glassy sheen.

A bright and clear blue sky during a winter day, a dark and ominous star was shining with a refreshing smile.

"Just as they say, if you laugh, you'll be blessed. Instead of pretending to be a solemn philosopher, I would have dug my own grave."

"Who's digging? Who's trying to dig their way to escape?"

Gyeon Poye looked around, but, not finding anyone digging, she just tilted her head in confusion.

Qing pulled Gyeon Pohee closer to her side and put her arm around her shoulder, while her white and long hand naturally went and burrowed into her bosom.

It was a super-speedy infiltration of a breast using the Wushang Divine Palm Technique and the Mysterious Hand Technique.

Yeah, boobs, boobs are the best.

But not mine. Only someone else's.

"Kyaak, it tickles."

Unlike her alluring beauty, Gyeon Poye was ticklish, twisting her body while laughing like a child.

While having a woman by her side and fondling her breasts, Qing spoke with a gentle voice to the general manager.

"General Manager? You were quite impressive. But I said one of you two should die, not that only one of you should die, right?"

The general manager had a look of utter devastation, desperately uttering in a broken voice.

"Th-There was no such promise-"

"Ahem. You should listen to what a person has to say until the end, you know?"

Qing cut him off and continued, her voice still carrying a trace of laughter.

"I was a bit depressed lately, but thanks to you, I had some fun. That was a great performance of beating an evil person. My score is… 96! Congratulations! You Passed!"

"Thank, thank you!"

"No need to thank me. You did a good thing, so you should receive a reward. Do not forget this moment and I hope you'll continue beating down evil bastards in the future."

"Yes, yes!"

"Instead, you don't have time to collect your assets and take care of your family, you hear? If you reappear before my eyes again, you'll die, so run away now, and far away. Got it? Promise?"

"Yes! I will! I'll run away right away!"

"Okay, then. Now get lost."

At that, the general manager hurriedly ran away. All the kneeling he had done until now seemed to have been to build up momentum for his escape.

"Ah, that's right. Um-mae? Where's that guy? That one who was guiding us. Hmm, I didn't even catch his name. Well, not like I care, but…"

"Ah, that guy? I just left him around somewhere……."

Qing turned her gaze to where Gyeon Pohee was looking.

But all that was there were the groans and moans in a chaotic mess, with the wounded writhing under the fishing nets.