\chapter{When Mom Goes to the Island's Shade to Pick a Head (9)}

In just a few days, two of the groups known as the "Three Great Unorthodox Sects of Guang Province" had fallen.

However, in the case of the first to fall, the Golden Caltrop Sect, despite the shock, the reason could be explained logically, rationally, and empirically.

It was the curse!

The curse of the people of the Jin Family who had died unjustly!

The Golden Caltrop Sect was massacred overnight.

There were no witnesses, and the most anyone had heard was a few screams during the night.

So the logical conclusion was that this was not the work of humans.

It was something done by ghosts, and specifically the work of a powerful ghost.

So the people of Guang Province felt something akin to joy and delight, rather than shock.

Those who deserved to die, died well!

There really is something like divine punishment after all!

Serves them right! It is a tragedy of my life that I did not see them die with my own two eyes!

However, the shock of the Guang Province Shrine's fall was different.

General Xiang Yu, filled with rage, descended to Earth by possessing a shaman's body. He had invaded alone, torn down the signboard, stained it with blood, and shown clearly to all under the heavens the end of evil men.

For an entire day, justice was served.

The people of Guang Province saw it with their own eyes, and some even joined in the looting and personally dealt with their enemies, who were writhing like worms.

By the afternoon, commoners who had grievances against the Guang Province Shrine had turned up and were showing off the Shamaness of Earth and Wood, acting as guides.

They even grabbed each other by the collar and fought, arguing over who would lead the way to their respective enemies first, before they could run away.

So how did the public in Guang Province feel?

Look here, the Shamaness of Earth and Wood-

Hey, is the Shamaness of Earth and Wood your friend? You should call her Divine Maiden! Please call her Divine Maiden!

Regardless of all that, by the time Qing finished her laborious yet rewarding work and lay down on her cot, it was already nearing dawn.

She had only closed her eyes and taken a few breaths, yet when she felt like she had just drifted off, a knocking on her door woke her up.

"Ugh, who is it at this ungodly hour……"

Of course, it wasn't dawn yet but just before noon, as the sun was about to climb high in the sky.

After all, Qing had only just closed her eyes, breathed twice and instantly started snoring.

"Who is it?"

Then, an answer came.

"S-Senio- No, Divine Maiden? It's me, Jin Seol."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Originally, Rising Stars often caused incidents.

This was because they were young.

As members of the Orthodox Wulin, who walked the path of righteousness, you were to pursue good, protect the weak, and not be silent in the face of injustice.

This was a teaching that the Orthodox Wulin repeatedly instilled in their successors until their ears bled.

In addition, they were children who had grown up hearing the heroic tales of the sect's revered seniors.

But even so, the reason why these incidents rarely escalated into anything major was because a Rising Star's martial prowess never strayed too far from that of the Rising Star level.

So-called famous individuals were at the Late Stage First-Rate at best and those who were exceptional prodigies (or promising talents who had consumed elixirs like they were eating rice) reached the Early Stage of Transcendent Realm.

However, in the current era of Wulin, Transcendent Realm Masters were practically as numerous as dirt.

Since it had been long since martial arts were codified into a systematic technology, even the most foolish person under the Heavens could reach the Transcendent Realm if they just kept at it with consistent training.

Furthermore, Jianghu had been at peace for a long time.

Since there were many martial artists who had lived long, there were also many Transcendent Realm Masters. So much so that even a small city would have one Master at that level.

This meant that even if a Rising Star caused trouble with boiling blood, there were always those who were capable of stopping them.

Through that process, Rising Stars would awaken to the true ways of Jianghu.

A chain of grudges, where one cut and another retaliated, leading to an eternal cycle without end.

Of course, they didn't properly understand it, but instead were just at the level of having a vague, intuitive grasp on things.

And then they realized that their martial prowess was not as great as they thought it was.

Furthermore, when one saw the line of responsibility that extended to the leaders of the sect, they began to realize their own place as a member of an organization rather than as an individual.

And this was how the Rising Stars of the Orthodox Faction, the kids, would grow up.

And so, Jin Jagang greatly reflected.

Ximen Qing was also a Rising Star in the end.

When he thought about it, she was only twenty-one, and it hadn't been even a month and a half since she turned twenty from nineteen.

He had not even thought about her age because of her deep, adult-like maturity, which allowed her to understand people's hearts and give comfort.

The problem was her martial prowess.

The incidents caused by the Rising Stars of the Orthodox Faction were, if to compare it to a child, the same as swinging wooden swords.

At best, they would cut down some low-ranking thugs, something that even the Unorthodox Faction would brush off and say that it was just bad luck.

The more dangerous ones were usually restrained, and if they happened to touch upon a higher ranking thug, they would get thrown back home as the Orthodox Faction's strength was strong.

Of course, the first trip to Jianghu was also the time when many young hot-blooded martial artists lose their lives.

But Qing wasn't wielding a wooden sword.

She had a real sword, and an exceedingly sharp one at that. So what was the result, now?

"Hmm."

Jin Jagang chose his words carefully.

He had summoned and seated her already, but found it difficult to begin the conversation.

So, did Qing do something wrong?

No.

Jin Jagang started from that point.

"First, I must say thank you and also that I'm sorry. What should have been done by the Jin Clan ended up being pushed onto the Heavenly Flower Sword."

"No, it's… The Jin Clan must also be in a very difficult situation……"

After saying it out loud, Qing immediately trailed off, wondering if it was the right thing to say.

Jin Jagang gave a bitter smile.

How would a clan head feel upon hearing a guest saying that they were having a difficult time?

"No. If the Heavenly Flower Sword can do it, then I too, could have done it. But… I wouldn't have done it. There is a family I have to protect. You could also say that I abandoned them to protect myself."

"No, that is only natural."

"Umm."

Jin Jagang picked his words, realizing that he was playing an awfully unpleasant role.

In fact, it would be more appropriate for him to praise her, to pat her head saying she had done a good job, and to celebrate her magnificent achievement.

But that was not an option.

Qing said herself that she was beyond the Transcendent Realm, but in truth, once you went beyond the Transcendent Realm, you would just end up being in the Unrestrained Realm.

Of course, that may have led to a different outcome than Qing, who had no trace of mercy in her swordplay. However, wouldn't he also have done nothing if he couldn't even destroy one Guang Province Shrine?

If Jin Jagang took the lead, the Unorthodox Sect would not sit still.

A Master of similar status would challenge him for revenge, and to save face, he would have to send out a figure that could absolutely win against the challenger.

After making a challenge, be it a life-or-death duel or whatever, they would either disappear into a rural area or fight to the death.

As a member of one of the Ten Noble Clans, it was an unavoidable challenge and if he accepted, how could he guarantee the clan's safety?

In truth, he already knew of the Guang Province Shrine's tyranny.

It wasn't as if Jin Jagang was planning on just letting them live like that. Once the Jin Clan had restored its power, he had intended to destroy those petty pirates and stop their tyranny.

But what about the people who had been suffering in the meantime?

So, the role Jin Jagang was playing now was that of an old man who had to tell a child that it was necessary to be cowardly and that the way of the world was such that one would have to resort to dirty and shameless actions.

"The Heavenly Flower Sword is not just one person. You are a representative of the Rising Stars as well as a dragon of the Orthodox Faction. You are also a direct disciple of Godmother, no, I mean Senior Matriarch and the one who represents her intentions, and you are also a disciple of the Divine Maiden Sect. Do you understand what I mean?"

"Yes."

"Even if you understand, listen once more. All the actions of the Heavenly Flower Sword are a responsibility of the collective, and its intentions, as a member of that collective, can be the collective's responsibility."

"Yes."

Qing's eyebrows drooped.

She wasn't a child who would just protest such words.

This was because she was not a child.

An individual belonging to a group could represent that group, even if that individual was only a single person.

The protest that they were only a part of it was nothing more than a weak and unconvincing excuse compared to the responsibility of the group that failed to cleanse itself.

Qing's expression was honest.

At that, Jin Jagang smiled gently.

If she knew her responsibility, then there was no need for further nagging.

"Still, it's fortunate that it was the Shamaness of Earth and Wood, who was possessed by General Xiang Yu, who had done it and not the Heavenly Flower Sword."

"Huh?"

"Let the Shamaness of Earth and Wood leave soon. You can say she left for Huadu by carriage, right? It has nothing to do with the Heavenly Flower Sword."

She should go to Huadu, a city to the north, in the disguise of the Shamaness of Earth and Wood. And then, she should buy a carriage and leave to anywhere she wanted. Then, she would return in secret.

That meant the Heavenly Flower Sword, who was staying at the Jin Estate, didn't know anything, and she was merely resting there as a guest.

Qing asked back with a dumbfounded expression.

"Uh, is that okay?"

"Who will know where that elusive Shamaness of Earth and Wood went?"

"But, what if they blame the Jin Family for it? Like, the Unorthodox Alliance or whatever."

"We'll just say we'll accept it if they have proof."

It meant that they would just insist on it anyway.

Wasn't this method similar to what Master would say to me? That if you get caught for using Demonic Arts, you should just insist that it wasn't Demonic Arts.

What is this? Is this the method used by the Orthodox Elders?

"To say it again, the Heavenly Flower Sword did what she needed to do. Even if it was somewhat excessive, those were evil people whom we could not suppress, thus they deserved to get killed. Rather, we should express gratitude."

Then, the Jin Clan Leader bowed deeply.

It was a scene not befitting to be shown to a mere young junior at the Late Stage First-Rate.

It was the second time he had thanked her so greatly.

However, Qing's expression was not all that refreshed, but rather rather reluctant as she left the Clan Leader's residence.

It was because it was not the type of reprimand that she had expected.

The rebuke that Qing wanted to hear was not that she should be careful, as if a careless action would cause harm to the people around her, and to be more cowardly and shameless while remembering that.

Was it something like the preciousness of life?

Or that instead of eliminating, she should try saving, and that instead of shutting their mouths, she should try to change their hearts?

Or perhaps that Killing Karma would inevitably harm her, so she should refrain from it?

But instead of such words, she had heard words that said thank you for doing the job they should have done, and that she had killed those bad people for them.

It meant that the act of killing evil people was a good thing.

But, is this the right path?

And what about those guys from the Guang Province Shrine?

Why were they, who were genuinely deserving of death, so utterly worthless?

Shouldn't there be some backstory, some melodrama, some things they worried about, some depth?

When they died, they were just met with joy and a clamorous celebration of the Guang Province Shrine's destruction.

Something… doesn't this seem… right?

Why do I have this so unsettling feeling?

If the dantian could make a sound, it would have been an absolute, enraged shriek that was pouring out of Qing's dantian.

The True Qi, which was meant to cleanse the spirit of Daoism and Buddhism, was running through the meridians as it continuously wept tears.

At the forefront was the True Qi of the Great Buddhist Saint, wearing a Buddhist robe, and behind that followed the True Qi of the Red Phoenix Goddess wearing a scarlet robe and then the Yijin Cleansing True Qi, who was displaying a bare chest under a tattered Buddhist robe, all while riding in palanquins carried by dragons and elephants.

And when the Daoist True Qi reached the top, the Upper Dantian's floor was filled with the chittering of demon sounds, scattered like malicious musical instruments.

As the Daoist Divine Arts crushed them, the demon sounds stubbornly welled up, showing no sign of diminishing.

Even after they spent the last few days so peacefully, why did they suddenly start raging like this?

True Qi should flow freely, and not be stagnant, so there was no stopping it.

They had no choice but to do their task and return back after their trip to the top and entering the dantian's door.

Then, the demonic energy, taking delight in their situation, would laugh at them, as if saying that they had no one but themselves to blame.

Usually, the Blissful True Qi would glare with narrowed eyes and maintain the rules, but the most overworked person at the moment was the Blissful True Qi, making it hard to even see its face.

And in one corner, the Heaven-Shattering Demonic Qi, who was stuck there like mold, just went, "Hehe."

Then it happened.

Bam! The Blissful True Qi, having spun around once and returned through the Dantia's door, rushed and scattered its translucent robes to the side, kicking the wall.

It was Blissful True Qi's side kick!

It kicked the side of the Heaven-Shattering Demonic Qi, who was curled up facing the wall, with a loud thud.

And then, it kicked its way back out again and rushed to the top of the Baihui acupoint2.

Busy, busy, turning Killing Intent into Lust, Blissful True Qi had barely a moment to breathe.

At that, the Daoist and Buddhist True Qi let out a huge sigh and rushed back out to clean up the Demonic Energy once again.

The Demonic Energy, which had been momentarily startled at the appearance of the Blissful True Qi, turned its gaze to the Heaven-Shattering Demonic Qi, who was lying down.

The Heaven-Shattering Demonic Qi was twitching as it lay on the ground, clutching its side before it then crawled back and resumed its squatting position facing the wall while snickering and chuckling.

The Heaven-Shattering Demonic Qi was smiling.

And the Yue Maiden True Qi silently observed this scene.

Without any expression on its face.