\chapter{When Mom Goes to the Island's Shade to Pick a Head (2)}

The Alleged Supreme's smile was rather fierce.

After all, human nature itself was such that they were inherently cunning beings. And separate from the Supreme Pretender's level of martial skill, they were still human beings, which meant that strange thoughts could not help but surface.

But, was this all his mother amounted to?

The giant that he remembered who'd scolded him so harshly, that was nowhere to be seen.

The woman before him now was just an extremely beautiful, young girl.

The Supreme Pretender pondered over this, a feeling slowly rising within him, and finally concluded what it was.

Disappointment. It was disappointment.

However, he quickly changed his mind.

No, that wasn't it.

She was already his mother. Even if she was insignificant, she was still his mother – the mother he yearned for so much.

The one thing that he didn't have, the thing he needed, the thing he had to have, the thing he so desperately wanted.

So this had to be it.

It was fine if she was insignificant now.

He could cultivate her into his ideal mother later on.

If Qing knew, she would have said something along the lines of, "What kind of freak is this?" But since the current state was terrifying, she would only grumble to herself.

But the Alleged Supreme was originally a person like this.

It was possible that this was due to the lack of family education.

As such, Qing gulped.

Something felt off. In a short span of time, hadn't this punk's gaze become more disrespectful and dangerous?

No way, was the son pretender going to change his profession and become a rebellious pretender?

Qing awkwardly forced a weak smile.

"Hehehe. You know, all of that was for your own good, right? To be righteous and upright? Thanks to me, you're a new person, right? You became a Transcendent Realm Master, you became younger, and even more handsome? Whoah, a triple win, like eating a pheasant, a pheasant's eggs, and taking its nest too."

At this, the Alleged Supreme grinned.

"You are right. However, that was also the first time in my life that I had ever experienced that much pain. Even now, when I think back to it, my dantian aches and the eye socket I lost throbs."

"Ah ah. It still hurts."

Shit. I should have killed him back then.

In fact, that was why I kept him alive.

I wanted him to remember me every time his dantian hurt and his eye throbbed. I wanted the pathetic cripple that lost his dantian to struggle with the pain of powerlessness.

To see an unerasable scar, a lifelong wound that he couldn't get rid of.

But…

He came back as a Profound Realm Master?

Still, it's better than having him come back as someone who's out for revenge. Right?

No way, this isn't revenge, is it?

"But, wasn't that the precept that Mother bestowed upon me? I always regret my foolish past whenever the scar stings and aches."

"Hmm. I see."

I think I'm regretting it too, though.

No.

I am regretting it.

I should have killed him on that day we quarreled, when he was still pathetic.

"There is no need to be so afraid. What kind of mother would be afraid of her own child? A mother! Is one who, even when she knows that a child is hurting, punishes the child with a pained heart."

"Yeeeaa, i-is that so?"

"However, if you were not my mother, then that is a different story. How important is one eye to a martial artist? So that's why I imprinted the feeling on my bones because I recognize your role as a mother! If not, you'd just be an enemy, wouldn't you?"

Qing's spine felt a chill.

Why did he emphasize ‘mother' and ‘child' while placing so much emphasis on them?

This has to be a threat, right? He's threatening me right now, right?

No way, is he threatening me into becoming his mother?

Am I the first person in the world to be threatened into becoming someone's mother?

Actually, that wasn't true. There were people who have been threatened into adopting someone as their son in order to have them inherit the throne.

But Qing didn't know.

So she thought, just what kind of cruel fate was this? Why do I have to be in this state after traveling such a long distance to this unknown land?

"Hmm."

"Mother, are you also not happy? Your obedient son is a Transcendent Realm Master. You wanted a good son, so I became a good son. If you want another kind of son, I can also become that. I heard you enjoyed eliminating evil, just tell me."

At that, Qing's expression hardened.

As terrifying as it was, what wasn't right still wasn't right.

Even if he was an adopted son instead of a real son, or a friend that she had a strong bond with, he shouldn't just take advantage of and throw away someone because of his own needs.

"What kind of dogshit is that, I mean. I never said be my son. What are you, recruiting a loyal subordinate or servant? A parent is a parent, and a child should live their own life. So you are going to use a child, keep him by your side, and use him like a tool? What kind of mother is that? If that's the case, you should just leave if you have nothing else to do. What the hell am I even listening to right now?"

At that, the Supreme Pretender's smile grew deeper.

It was not a good sign.

"That is strange? Didn't you say you wanted me to be a good son and that you would love me if I was good? Wasn't it you who wanted a good son?"

"No, I didn't say it in that kind of way. You're twisting my words, aren't you? I said I'd be pleased to see you again if you were good."

"If I was bad, then you would have hated me, wouldn't you?"

"Tsk. Of course it's only natural I wouldn't want to be close to a bad guy. What's wrong with that?"

Qing's expression crumpled.

"Putting aside your words about me being your mother, it's only natural for parents to tell their children to be good, right? What do you think I'm hoping to gain from you by telling you to be good? I can tell that you did a lot of good things. You can't feel anything from doing that? You didn't see that perky little kid earlier? Don't you ever think, ‘Since she likes me, I like her too'?"

"That kind of thing…"

Suddenly, the Supreme Pretender's eyes trembled.

Flashes of faces suddenly passed through his head.

Though the degree and depth were different, there were looks on the faces of the cult members who smiled at him, those gazes that overflowed with affection and sincerity.

Yes. It was different.

It was an affection, an understanding that was completely different from the fake smiles that he received when he was a Supreme. All those looks were made of fear or greed.

There was trust.

That was it.

He no longer needed to yearn for affection.

Because he was already receiving it.

"I see."

The Supreme Pretender suddenly felt the massive lump that had been filling his chest and constricting his breathing slowly dissolve.

And then, the Pretender's smile changed into a genuine smile.

It was no longer the fierce and savage smile of a sharp blade, nor was it the baring of fangs and stretched lips of a wolf, but instead it was like a genuine bright smile of a child.

Qing's heart felt at ease for a brief moment upon seeing that smile.

Just for a brief moment.

Because the Supreme Pretender's expression had turned into one of a mischievous imp, a prankster with a face full of mischief.

"This! This is what motherhood is all about, then!"

"Eep."

"A heart that wishes for her children to do well, that wants her children to be loved! This son was foolish! How insignificant. How insignificant were the martial skills of an individual! Mother, ah, Mother. Indeed, my mother is the only mother in this world! Please accept your son's bow!"

"N-No, why are we suddenly going there again? And you did just say ‘insignificant'-"

"Come to think of it, children don't necessarily have to be acknowledged by their mothers, right? Mother, you have molded a new person through your teachings, so even though you didn't physically give birth to me, it's no different than creating a new person in this world. So I am already your son."

"No, why are you deciding this all by yourse-"

"I am already your son. I will not ask for your permission to do so."

And then, he grinned slyly.

Qing, at a loss for words, just opened and closed her mouth.

But what the hell? Is he serious?

Somehow, there's a subtle change in his attitude from earlier.

Up until just a moment ago, there was a sort of extreme drive? A desperation? An ambition? Some kind of extreme obsession that could be seen.

However, now it felt vague whether his words were sincere or just a joke. It had become so light and jovial.

Just as much as the Supreme Pretender himself seemed to have relieved himself of some weight and felt refreshed.

"Since I was young, I have had one wish, to have something that almost everyone in the world has that my I alone lacked. How sorrowful. There was a life-long dream of mine, and that was to call out for my mother. Will you allow me to do that? Even if you don't, I will still do it, though."

"Then, why would you ask-"

"Mom."

The moment she heard the word, chills surged throughout Qing's entire body, and a pure scream with maximum clarity without any impurities burst forth.

If there was a painting representing the screams of an artist who was not even born yet in the West, it would be the image of the human Ximen Qing.

"Eeep, d-don't do that, don't do it."

"Mom. Mom! Hah, wow, this is great, huh? Mom? To think that only those with a mother were able to use this. It's frustrating that I couldn't do this up until now. I'm going to have to do this for as long as I couldn't do it until now. For the next 50 years, it seems. That's alright with you, Mom, right?"

And then, as if realizing something, he slapped his hand with his own fist.

"That's right. "Mother" is a more formal and awkward term, but "Mom" is just Mom – the most intimate address in the world. It feels so comforting."

"No, it's comfortable for you, but not for me. Seriously, I'm not kidding, please stop doing that. Wow, chills, can't you see the chills?"

"Hmph. It's my choice. Hmm. I like it. Mom? Shall your son do a little song and dance?"

"I'm going to go crazy, really."

Qing said this and averted her gaze.

She had created a son, and a son who was far older than her. No, wait, what was I saying about ‘mom?'

"Mom."

As soon as she heard that word, the chills returned again.

I can't take this. Help!

Though it didn't seem like there would be much help, Qing looked at Gyeon Pohui with pleading eyes, grasping at straws.

"Huk, how touching. Nephew, you don't have to be so formal with me, calling me Auntie. You can just call me Auntie."

"Okay, Auntie."

"Is using honorifics a bit much? Usually you'd just be casual with a younger auntie."

"Okay, Auntie."

As expected, she wasn't any help at all.

No, instead, she's throwing more fuel on the fire!

"So, Mom. Your son has waited a long time. Please give me a name."

"Ugh, c-could you at least call me Mother?"

"Do you like the formal version? Is a son who is like a friend not good?"

"I just don't like being a mom. I just don't like it……."

"That is rejected. How can I sever such a heavenly bond? But if Mother wants it, should I use honorifics?"

"Let's just keep it casual, keep it casual. If I hear honorifics, it'll feel too real. Ugh, my stomach hurts."

"If you want it to feel real, it must be with honorifics, huh? But since you dislike it, let's settle with a semi-formal address."

Qing pressed her temples, making a terrible face.

At this, the Supreme Pretender jumped up.

"That is a serious matter, Ack! Stomach! Mom's stomach! Is this childbirth? When did you even get pregnant, Ack! A sibling! So, am I going to have a younger sibling now!? When, when will they be born?"

At this, Qing's eyes lit up with anger.

"What? You have a mouth, so you can say whatever you want? What are you talking about? My stomach just has a bit of bloat because I ate a lot, okay?"

"There is no need to be ashamed of it. No, wait, how could your stomach swell so much just from eating? In the first place, no one's stomach swells up that much even when they eat like a glutton, and besides, who eats so recklessly and mindlessly?"

"Shit, is that your problem if I'm eating? Did you add anything to it?"

"Eiii, Mom. We're already family, right? A sibling, a sibling. How lovely. What should I do to be a good older brother? No, wait, is it an older sibling? What will the doctor say?"

"Seriously? So I'm getting another sibling?"

At this point, regardless of whether she reached the Transcendent Realm or not, Qing was slowly starting to feel her anger rising.

And with the insight of a coward who targets the weak while coddling the strong, she knew that the Supreme Pretender didn't seem like he'd cause any harm.

"You motherfuckers are both being such a pain! Get lost! Please!"