\chapter{When Mom Goes to the Island's Shade to Pick a Head (5)}

A new signboard was raised at the Jin Clan.

天下振家. Tianxia Zhenjia. Under Heaven, Zhen Clan.

Four characters filled the frame in a grand way.

Well, at least it's written.

Qing was still cautious.

While everyone was making a fuss over how good her handwriting was, from Qing's perspective, it was just ordinary script that she always saw back in her hometown, was it not?

Having never studied calligraphy, she had no philosophy or thoughts regarding the shapes, so wouldn't it just be an empty shell that only imitated the outer appearance?

Although she'd acquired martial arts in a different way from other martial artists and freeloaded, the enlightenment itself that took her to the Transcendent Realm wasn't something that had come from within her, after all.

So, her making such a fuss over the "Transcendent-Transcending Transcendent-Super Transcendent Qing" persona was basically just her way of being proud of something she had done herself.

While she did rely on her monstrous physical abilities for her carpentry, she learned the tricks herself from watching and doing it. The same went for her work as a physician.

But with calligraphy, she had never put any effort into it, so she just wrote whatever came out, and yet those around her were frantically drumming on their foreheads and making a big fuss over it.

It was as if they were making such a big deal of it just because she was breathing, leaving her unable to shake off the embarrassment.

However, Jin Jiaju was just beaming with smiles.

Jin Jiaju was originally an affable man with a smiling face, but this was the most ecstatic expression that Qing had ever seen from him.

"Is it okay if it's not a signboard script?"

There were specific scripts that were supposed to be used for signboards.

It wasn't as if it was mandated by national law, but it was on a level where it was to be done as a matter of course.

Otherwise, people would finger-point and say that she'd used a script without a basis for the signboard, mischievously messing with the very first impression of the group.

"This is a script that is better than any signboard script I have ever seen in my life. I will guarantee it."

But for people in Zhongyuan, Qing's hometown's standardized script was practically a brand new world that would make their eyes pop out.

It was not just some random script done with gravitas, but a style of calligraphy with a profound history etched into each and every stroke, thus properly establishing its form.

Even though there were scripts that were supposed to be used for signboards, wouldn't the calligraphy written by someone high up like a virtuous high monk or even the Emperor be considered more precious than that?

Qing's calligraphy was worth that much.

In truth, even if Qing's calligraphy was so bad that it would be considered a doodle instead of writing, it was still a script personally bestowed by a Princess, was it not?

"I would like to treat you as an honored guest to a great master, but wouldn't the Heavenly Flower Sword be a bit too much?"

"Yes."

Jin Jiaju smiled, as if expecting that answer.

This unassuming young prodigy was incredibly harsh on her own abilities, always being so humble, saying, "Is that all?"

There was none of the arrogance common with young masters, the conceitedness that stemmed from their confidence.

How could one not find her lovely?

How did a disciple like this, a veritable goddess, come from the likes of Senior Mad Dog!

How could the Heavens have created Mad Dog and then made the Heavenly Flower Sword her disciple?!

Envy! I'm so jealous I could die!

The luck of one's children was the greatest of all blessings, and children and disciples were not that different.

The Godmother had not shown even a shard of her ‘Mad Dog' nature with her smiling, elder-like attitude at the Wulin Tournament. So it must be thanks to the disciples that have had her luck in her twilight years.

Although his sons were said to be righteous and well-behaved due to taking after their gentle and composed father…

In a father's heart, the praise that their children were good people by nature always sounded like an insult, implying that, well, they were otherwise… lacking.

The gaze of Jin Jiajiang as he looked at Qing was truly like the sparkling, pointed diamond from a storybook in Qing's hometown.

Feeling heavily burdened, Qing quietly averted her gaze.

Jin Jiajiang's attitude was not excessive.

The eyes of the Jin clan members looking at the signboard were bloodshot.

The crooked signboard represented the Jin Clan's broken will to fight, but it was also a memorial to their deceased family members.

As such, the hearts of those in the Jin Clan looking at the newly formed four characters were not just ‘Oh, we got nice calligraphy'; it was that it gave them a vague hope of things getting better from now on.

Whether it was because they truly liked the calligraphy or in order to show off that the Jin Clan was still standing tall, they even unusually flung open the front gates.

Considering that a mere commoner or laborer wasn't allowed to enter through the main gate while carrying their tools, it was a truly unconventional step.

"Wow, the calligraphy is amazing, huh. I wonder how much something like that would cost?"

"Dream on. It's not just about having gold and silver, you know? It's all about the connections, the connections."

"Who said I wanted it? I was just curious about how much just one character on a scroll would cost. Why didn't our ancestors leave any of them behind, I wonder?"

"That's because their descendants had eyes only for money and would sell them all off. I say! The characters look so very sharp and piercing. This is the power of the Guangdong's Number One Family, right here!"

Thus, the Jin Clan's full-scale construction began.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The restoration of the Jin Center began with the walls.

After removing the old roof tiles, new tiles that had never been used and that gleamed were placed.

If they sprinkled seawater on the walls, wiped away the dust, and applied ashes to redecorate it, even if the inside still stank like a barn, from the outside it would at least look like a newly built wall.

It was as if the Jin Clan was stretching and showing off its full power.

The Son Wannabe had disappeared somewhere along the way. Qing thought that he had probably just been reluctant to help with the restoration work.

After all, he was someone who had been calling himself the master, or whatever, you know?

She couldn't imagine him mingling with the laborers while carrying roof tiles and piling them up.

Gyeon Pohee, on the other hand, seemed to be happy as long as Qing was around, no matter what they did.

But Qing wasn't having any fun.

It wasn't a job that required any particular skill, nor was it an activity where she could enjoy the satisfaction of using her hands.

Painting the walls only brought back bad memories, and laying roof tiles was just a series of simple, repetitive tasks.

And what was even more bothersome was the Righteous Karma of the adopted sister, whose numbers were approaching 500, constantly getting on her nerves.

When they first met, the adopted sister had just a little over 100 points of Evil Karma, but now she was about to reach 500 points of Righteous Karma.

But the adopted sister might be somewhat lacking, but her nature itself couldn't be considered evil.

But seeing Gyyeon Pohee's numbers made her inevitably think of Hwiyoung Yeom's numbers as well.

But what about that Son Wannabe?

Could 1000 points of Evil Karma be substituted with 1000 points of Righteous Karma?

If someone accumulated 1000 points of Evil Karma and 1100 points of Righteous Karma, leaving them with 100 points of Righteous Karma, could that person really be declared to be good?

Or conversely, if someone accumulated 1000 points of Righteous Karma and 1100 points of Evil Karma, causing their numbers to go over a hundred, showing up in red letters, would that mean it was okay to just keep tormenting and kill him, since he was just an evil person?

Was it really an issue that could be solved by simply adding and subtracting and arriving at a conclusion, saying ‘Okay, so the Jeweler has 30 gold sycees worth of loss?'

A hallucination of the Celestial Martial Emperor, or perhaps it was the Martial Ancestor Qing, who snorted at her for speaking such stupid things.

How could that old man be so certain and dismiss it as such idiotic nonsense?

Qing's hands, which had been laying roof tiles, slowed down and then stopped, staring blankly into the distance.

Her hands trembled. Gyyeon Pohee, with a worried look on her face, asked.

"Unni? Are you hurt?"

"Huh? No. I'm just… feeling a little…"

"Feeling? Oh no! What should I do? Should I hug you?"

"Uh? Yeah."

Being hugged in the adopted sister's arms, she felt somewhat calmer.

But should she keep putting it off?

Ever since learning the truth about Hwiyoung Yeom, she had been trying not to think about it.

Thankfully, that shock was so extreme. Uh, eww, just thinking about it sends shivers down my spine.

Or was it just me? Was I in the wrong? If the hole or Nanah was my mother, would I have shivered so much? Isn't this a sign of misandry?

No, no. Don't try to run away from it again.

Qing pulled back the thoughts that were trying to flee away as if by instinct.

I have to come to a conclusion no matter what.

Even if I try to ignore it because I don't want to think about it, there will be a time when I won't be able to avoid it.

"Clan Lord, I think I'll head in early today."

"Are you alright? You don't look well."

"Uh, a little. So I'm going to rest early."

"Hmm, I'd like to give you the guest room, but it must still smell like shit there. Rest well, and if you still don't feel well, then there's no need to come out, so focus on your body first."

Jin Jiajiang encouraged her to rest in a kind manner.

And so, while resting in the adopted sister's arms on the comfortable bed, Qing tried to organize her thoughts. Hmm.

If I do a lot of good, would it be okay to do something bad?

If my Righteous Karma reaches 1,000 Points, would it be okay to kill a kind civilian for fun and knock off 100 points, leaving 900 points remaining?

On the other hand, that felt like an absurd leap of logic too.

The way people live was not a series of choices of this or that, like selecting from options on a screen.

People with high Righteous Karma would just keep accumulating more Righteous Karma if left to their own devices, because good people would continue to lead a good and virtuous life.

The same would be true for evil people.

Unless there was a sudden mental breakdown, or a shocking turning point akin to that.

But they could change, right?

Everyone has changed, haven't they?

The adopted sister, that Son Wannabe, Gramps, the fugitives from the Seol Clan.

Was there a chance for all the evil people I had killed, those I had enjoyed tormenting and left out like trash, to change as well?

Am I, am I really a righteous person?

A demon, no, a pleasure-seeking killer. I just got lucky, that's all…

"Unni? Unni!?"

"Huh?"

A desperate voice called out to her. When Qing came to her senses, she found that she was in Gyeon Pohee's arms, being held tightly as if she would break.

"Unni, you were trembling so much. You were sweating so much. Are you okay? Are you hurt? Did you have another seizure? Was it like when you were in the Divine Cult?"

Gyeon Pohee's expression as she gazed at Qing was on the verge of tears.

Qing, whose reflection was in Gyyeon Pohee's eyes, also had the same expression, but she failed to notice it as she averted her gaze and bowed her head.

Ugh, I knew it. I shouldn't have thought about it.

However, one's thoughts are not something that would simply cut off one's interest simply because they didn't want to think about it.

Therefore, even if she tried to shake them off, the nasty thoughts that she didn't want to think about kept following and nagging her.

Qing finally made a decision.

"Unni. Can I touch your breasts?"

It was embarrassing, but wasn't escaping also said to be helpful?

I really don't know anything anymore.

Should I trust these numbers?

Even if I do, why, why are they telling me that this person is a bad guy, and this person is a good person?

If they were going to show it anyway, why not just show Evil Karma and Righteous Karma separately?

Why are they combining it and making me confused, annoyed, and disgusted?

I don't know anymore. I'm just going to touch breasts.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As the full-scale restoration of the Jin Center began, another group found itself facing a crisis.

It was the Guangzhuo Hermitage.

The Salyue Clan was observing for now. The Jinjok Clan had been struck by a major disaster, which was currently ongoing.

But they didn't know each other's situations.

The relationships between the three unorthodox factions weren't good.

No, it wasn't just that they weren't good, but the fact that they were even grouped together as the three unorthodox factions was displeasing to each other.

There could only be one tiger on one peak. (The opinions of tigers could differ.)

Once the Jin Clan was driven out, only one force would end up seizing the hegemony of the Guangzhuo territory.

As such, the Guangzhuo Hermitage Master was overtly playing it safe.

He intended to hoard his strength, watching how things went until the Jin Clan was pushed out, and then stab them in the back at the right moment.

Of course, because his intentions were so obvious, the other two forces were also seething with rage, reaching an unspoken agreement that, once the Jin Clan was driven out, they would join hands and utterly annihilate this bastard.

But, all that was a story for after the Jin Clan was driven out.

When the Jin Clan started to wiggle and stretch itself, ready to rise again, even the Guangzhuo Hermitage, which just wanted to watch and stab them in the back to take Guangzhuo, couldn't just watch anymore.

And originally, people lived as they always had.

Like kind people would always stop and help those in need, people with wicked hearts would also behave exactly the same way they always had.

Therefore, they just reused the method they had enjoyed before.

However, the situation was different from before and now.

At least when they pulled their tricks before, Qing hadn't been in the city.

And now, Qing was present.