\chapter{When Mom Goes to the Island's Shade to Pick a Head (5)}

Thump, thump, thump, thump. Someone impatiently pounded on the main gate from the early morning.

However, that sound, after crossing the wide garden of the villa and passing through the sliding paper doors, wouldn't be much of a disturbance to ordinary people.

But Qing's body was far from ordinary.

Even so, the reason Qing didn't wake up immediately was a sort of unconscious apathy.

It was because if she woke up at every sound she heard at night, just because she possessed superhuman hearing, she wouldn't be able to sleep even a moment.

However, the situation changed slightly with the addition of the pounding sound on the gate along with voices calling out plaintively, "Fairy, Heavenly Maiden! Oh, Heavenly Maiden!"

After all, people were more sensitive to sounds calling them, even in their sleep.

Qing opened her eyes in the arms of Gyeon Pohui.

The pale blue glow of dawn seeped in through the sliding paper doors, causing her irritation to rise immediately.

Just what kind of bastard was waking people up by pounding on the door like this from early morning?

However, the softness touching her fingertips calmed her anger a little.

After all, because she had fallen asleep without washing last night, and her hands had already burrowed under the bosom of the sister's jacket, rubbing her hands against her soft breasts like dough.

Hmm. I wonder why her breasts never get boring.

Qing remained on the bed, and with a still drowsy mind, gently felt her breasts, and was satisfied with how it felt.

While her hands were stroking her soft belly and groping the skin on her sides, she continued to appreciate her smooth skin-

Thump, thump, thump, thump. Fairy! Please!

But still the pounding sound.

Qing sighed and finally got up.

"Uhhh, oh My Sister? Did you get up alreaaaady……?"

"Ah. Did you wake up? Why aren't you sleeping more?"

"No, ugh, whaaa, I think someone is calling outside?"

"That sounds like it. Just stay here. I'll go check it out."

"No, I'll go too."

As she had fallen asleep immediately, she was still wearing the same clothes.

Her hair would be a mess, but hats were invented for times like this. (Not really)

Putting on a veil, Qing yawned widely as she opened the main gate, and despite it being early morning, many people were already gathered.

However, their expressions…

Qing felt her sleep completely fade away.

"Fairy, the curse, the curse has returned!"

"You said you had banished the curse!"

"My husband, Fairy, we have to hold a funeral, but in case the curse might spread, please ward off the evil spirits, will you?"

Everyone opened their mouths at once with their own requests, with some showing shock, others with resentment, and still others begging and crying.

Qing's face froze coldly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

While the guards kept the onlookers at bay, forming a human barrier around the area, Qing quietly slipped inside.

To the people, a shaman who was said to be powerful was a difficult and frightening existence.

Even though Qing slipped in, no one stopped her and just eyed her cautiously, making her entrance as natural as if she were a police commissioner.

Corpses covered with rough straw mats were lined up in the market.

The damage to the bodies was so severe that it wasn't even worth showing.

Seven corpses, and with another stretcher having just arrived through the crowd, that made eight.

Due to the swaying of the stretcher, an arm of the corpse fell off and rolled on the ground.

The scar on the back of his hand looked familiar.

Qing carefully removed the mat covering the corpse to confirm his face.

It was Carpenter Lee, or whatever his full name was, Although she didn't know his full name, he was a person she knew by face and had joked around with.

Of course, people like Carpenter Lee often got rich through various techniques.

Stealing small portions of materials, inflating costs, using transparent laborers who only existed on paper, and so on…….

So if Carpenter Lee was to be judged by his Evil Karma, he would be considered a borderline evil person.

But in Zhongyuan, if one called this kind of extortion "gouging," they would be ridiculed for being fools who didn't understand the basics of a merchant's virtue.

Moreover, he only swindled his customers, so as a carpenter, he was well-respected for using the stolen money to share with others, treating his employees well.

If this Lee was over 100 points of Evil Karma, he might have just died of natural causes.

But still, I'm angry, you know? Very angry.

Qing gritted her teeth.

Which degenerate bastards was it? So did the Killing Moon Sect finally decide they wouldn't be so careful anymore?

I should have just released the poison earlier.

Instead of hesitating, I should have just killed them all.

Flames of anger rose from Qing's eyes.

It was a flame that burned with colors that did not exist in Zhongyuan.

At that moment, a scene suddenly flashed in her mind.

The lamp light was blurry and the world was shaking, it was the sight of a truly intoxicated person.

Suddenly, unknown people were shoulder-to-shoulder, pretending to help. Before she could ask who they were, a sharp blade pressed into her side, forcing her silence.

Her vision became clear as if her spirit had been jolted awake. She was being dragged through an empty back alley.

They were stabbing, cutting, slashing. Amidst the gradually blurring vision, she could hear a cackling laugh.

‘Let's quickly finish this and go have a drink'.

And then, darkness.

Qing staggered.

"Oh My Sister? Are you okay?"

Gyeon Pohui rushed in and grabbed her arm.

Before she knew it, sweat had gathered at the tip of Qing's chin and dripped to the ground with a thud, thud.

What was this?

Did I become a real shaman after playing the part of a shaman? Possession? Superpowers? Precognition? Past lives?

Moreover, who was showing this to me?

Is it my ability? Is it you, Lee?

Or is it the Status Window, again?

What's the reason for showing it to me, of all people?

No. No, that's not it.

Why ask me why? The answer is obvious.

Qing's lips stretched wide into a grin.

Whatever their scheme might be, fine.

Yeah, I like this one, so I might even play along.

Qing's head whipped around.

After all, from the stories I've read, the culprit always appears at the scene.

Whether it's to show off, or because they are secretly trembling in fear over something going wrong, thus trying to observe the situation.

Then one unfamiliar yet familiar face came into view.

Qing put her arm in Gyeon Pohui's with a casual attitude, and then started moving as if going home.

Then, at a certain moment, Qing grabbed the man by the collar and flung him into the sky with all her strength.

"Uwaaaack!"

The man screamed as he crashed down amidst the police officers, landing near the head of a corpse.

At the same time, she heard a whooshing sound that tore through the air.

The hammerhead made a large arc and struck the man's ankle, causing a loud bang!

The bricks forming the road below exploded and flew into the air.

With the sudden commotion, the onlookers screeched out in surprise.

Regardless of the uproar, Qing grabbed the man, whose legs were now disabled, by the collar and raised her open hand high in the air, then slapped him, smack!

"Aaaaagh! Ack, ack, ack!"

The man, who was screaming from the pain and fear of having his ankle shattered, suddenly cut short his screams, each syllable breaking off like scattered beads.

Smack! Smack! Smack! Smack!

Soon, only the sound of Qing's right hand repeatedly hitting the man's right cheek echoed loudly through the silent marketplace.

Blood was already gushing from his ears and blood tears streaked down his cheeks. His eyes were barely protected, as Qing's monstrous strength was slapping his cheek over and over.

Before she knew it, Gyeon Pohui held the man's arms firmly and extended them forwards.

The man tried to resist, but Gyeon Pohui was now a proper Master, on the verge of reaching the Unrestrained Realm, and furthermore, she was a Great Protector of the Divine Cult who had learned a great secret.

She was not an opponent that some mere warrior could possibly resist.

"Stop, ack, please, ack, stop, ack."

But the hand slapping his cheek did not stop.

It was only when half of the man's face began to swell into a purplish mess that Qing finally dragged the man.

Gyeon Pohui, who was quick to read Qing's mind, immediately relaxed her grip, so the man's body limply collapsed like a puppet.

The man landed on top of Carpenter Lee's corpse.

And following that came a cold voice.

"Why did you kill him?"

"Wha, what do you mean."

"I'm asking you why you killed him."

Qing grabbed the man's hair, and forcefully brought his face close to Carpenter Lee's corpse, pulling down the mat.

The man shook his head in horror.

"Hieeek."

"Why? Why are you surprised when you're the one who killed him? You were happily giggling while killing him, but now you're scared of the dead body?"

The onlookers gasped or held their breath.

"Wha, what do you mean."

"You haven't been hit enough yet. Oh My Sister?"

"Okay!"

Gyeon Pohui grabbed the man again with a bright reply.

Qing raised her hand high in the air once more.

"Wait! Wait a moment! I'll tell you!"

"Too late. Ten lashes for now."

"Wait aaaaacck!"

Smack, smack, smack, smack.

The sound of flesh being struck rang out with a rhythmic beat.

With each hit, the sound of moisture began to mix with the sound, all due to the skin on his cheek tearing and blood flowing down.

After finally completing the tenth hit, Qing asked again.

"Why did you kill him?"

"I was, ordered, I was ordered too, ack!"

"Your voice is too quiet. Try again."

"I was ordered!"

"By whom?"

"By Master Weasel, ack!"

Slam! The man's head twisted to the side.

As he looked up with a wronged look, Qing responded with an even, monotone voice.

"If you talk like that, how am I supposed to know who that is? Are you only going to say things that only you know?"

"The Grand Master of the Tortoise Shell Unit! The Grand Master of the Tortoise Shell Unit, ack!"

"What's a Tortoise Shell Unit? Speak properly!"

"Master Weasel of the Tortoise Shell Unit, a combat unit of the Guangzhuo Floating Platform, ordered me to!"

At this, the onlookers once again gasped.

Regardless of that, Smack!

"You call that piece of trash ‘Master', huh?"

"No! That piece of shit Weasel ordered me to!"

"Why?"

"That was…"

Qing's hand rose to the sky again.

The man shouted urgently.

"They said if the workers died again, the Jin Family would stop the construction!"

"Who did you kill them with? Who did you kill?"

At this, the man immediately responded to Qing's words and started naming names.

In truth, Qing wouldn't know who they were even if she heard it.

But there were people here who were quite curious about them.

"Oh My Sister, break their arms and leave it there."

"Okay!"

Gyeon Pohui lightly snapped the man's upper arms, like breaking a twig, backwards.

Since one of his legs was already missing, even after Gyeon Pohui released him, he could only writhe on the ground without being able to even stand up.

"Let's go now. No, wait. Oh My Sister, it's dangerous, so why don't you wait at the shrine, no, the Jin Family compound?"

"No. I'm going with you to fight. I'm going with Oh My Sister."

Gyeon Pohui clearly expressed her intentions.

Qing opened her mouth but concluded that there was no point in saying anything because she wouldn't listen anyway.

"If it's dangerous, run away. If Oh My Sister is captured, I'll be in even more danger."

"Okay. Okay."

Although her face was covered with a veil, Qing could feel that the physician must have a bright smile.

Qing walked quietly toward one side of the marketplace as if she had finished her business.

The onlookers stepped back to make way, afraid to even touch her, and Qing strode forward with her characteristic swift pace.

"Ugh………"

The man was still crawling on the ground.

One of his ankles was shattered, looking like a ball of mashed dough, and with both of his arms broken, it was too difficult for any man with decent willpower to move.

And then, below the man, figures gathered, blocking out the slowly brightening morning sun, creating a shadow.

The victims who the man had proclaimed so proudly, their families, friends, and neighbors.

"Pl-Please, save……"

The man's voice trailed off.

After all, they were all holding the bricks that were broken by Qing's hammer, their hands clenched so tightly that their veins were bulging.

"Police, Police Officers! Save a person! Here."

But there was no answer.

If the police officers hadn't stood aside from the start, they wouldn't have been standing here.

And then, the obvious story.

The things they called revenge.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Surprisingly, it was clean in front of the Guangzhuo Floating Platform.

Qing tilted her head.

She thought there would be a bug bastard who'd hurriedly run back to their den and tell on them after witnessing her beat down the trash.

Or was I just being too underestimated?

Qing dragged her hammer as she approached the main gate of the Guangzhuo Floating Platform.

The sentries guarding the gate on both sides brandished their weapons and sucked in a sharp breath.

"Halt!"

Although there were two people sucking in air, there was only one voice.

It wasn't because the two had worked together so well that it sounded like one voice.

It was because the hammerhead made a large arc and struck an arm.

Her elbow struck the owner's torso, breaking all of their ribs.

The sharply broken ribs pierced through the lungs, creating a hole.

As a result, the person was rendered unable to speak.