\chapter{When Mom Goes to the Island's Shade to Pick a Head (6)}

"Hup."

The rest of the phrase, "It is the beginning," was forcibly omitted.

Kyeon Pohee's palm struck his sternum.

His chest caved in and as he was thrown backwards, the soldier barely moved an inch before his body suddenly stopped.

It was because a hand had fiercely grabbed onto his sleeve.

Although they held him in place and laid him gently on the ground, it was unknown what kind of trickery they were up to.

But in truth, they had only cleanly broken his rib cage to allow his sternum to sink in. As such, it was a gesture of consideration to allow the broken fragments not to pierce his internal organs, for him to live longer in pain without dying.

Qing, as a slaughtering devil who had already reached the peak of viciousness when it came to killing intent, could tell immediately. But for now, she was too busy calming down her coldly boiling rage.

Bam! The door shook and opened as if it was about to break down.

Two women entered the building.

Qing was tightly holding the signboard of the Gwangju Seonbang in her hands.

"Who, huh……"

Unfortunately, a warrior near the door, surprised, grabbed the handle of his dao.

But he was already one step too late.

The corner of the signboard, held vertically, was about to fall onto his crown.

Thud. Along with the sound of a watermelon breaking, the signboard, soaked in salt and oil from the sea breeze, pierced the disciple's head.

Red and white stains spread across the words ‘Gwangju Seonbang.'

Qing's gaze when looking at the collapsing warrior was as ordinary as if she was looking at a pebble on the side of the road.

She merely thought that there were definitely some who seemed to be running away when she had crushed one of them in the market.

How badly did they look down on people to be so unprepared even after seeing that?

Ah, but that's because the Gwangju Seonbang was a Bang, a group of people.

It was an organization made up of the ship-owners, dockyard owners, and village chiefs of the fishing communities of Gwangju.

As such, the bastards who had run away had scattered to their respective factions, seeking out their own elders in their mansions, so the news had not reached the main headquarters of the Gwangju Seonbang.

But what was Qing supposed to know?

She simply closed her eyes, thinking that they must have been enthusiastically training when hearing the shouts of multiple people.

Qing walked towards the sounds, carrying the signboard and dragging the hammer.

In the training grounds at the back of the flagstone path, the shirtless warriors of the Gwangju Seonbang were surprisingly having an earnest training session.

"One! Rising Waves!"

"Rising Waves!"

"Two! Rising Harmony!"

"Rising Harmony!"

"Three! Detach. Hup."

The instructor, who was calling out the moves on the training platform, was shocked as he swung his dao.

Clang! The blade of the dao, which collided with the hammerhead, shattered into pieces, covering the instructor.

As if that was not enough, the pieces of blade that flew past the instructor's face drew streaks of blood all over him.

"Who is it!"

However, instead of an answer, only the sounds of desperate screams reached them.

One of the disciples whose forearm was gone screamed, scraping his vocal cords and struggling to die.

It was a contagious scream.

The screams of a disciple whose knees had been broken and bent backwards, the desperate cries of those who were holding their spilled and dangling organs, begging to be saved.

Every time the signboard was swung around, a scream resounded without fail. The various blood stains on the Gwangju Seonbang sign finally dripped on the training ground's sand, forming red droplets.

"Stop! Stop this!"

The instructor shouted once again.

But this only made the damage worse.

The disciples flinched back in shock at his cry to stop, but Qing and Kyeon Pohee rushed in silently and tore, smashed, pierced through, and merely went on to the next target, and the next, and the next.

Finally, the instructor charged.

With a dao he had grabbed from a weapon rack on one side of the training grounds, he charged with quite a resolute expression.

"I will handle it."

The Yimae said as she stepped in front of Qing.

Qing slightly shook her veil as if answering her before turning her signboard against another warrior.

The Gwangju Seonbang signboard, which had been written in red letters on a yellow background, was now quite hard to discern as it was in red letters on a red background.

Screams and groans echoed through the training grounds.

In other words, it also meant that no one had died.

Since the dead had no voice.

This was because Qing's attacks did not target fatal acupuncture points.

"Aaaaa! Die!"

One of the warriors charged forward, boiling with rage.

Perhaps because he saw his comrade or his senior being hurt, his rage seemed to be on full display.

Qing looked at the warrior from behind her veil.

By seeing his feet, she could measure his steps and know the distance. By seeing his arm, she could see when he would extend his weapon, and by seeing his eyes, she knew where he intended to cut.

If she knew the distance, timing, and position, what would be so difficult about countering him?

It seemed like she was swinging her weapon around randomly.

But in that very instant when the warrior stepped forward, a signboard that subtly bent in the perfect angle struck him below the thigh, bending his knee.

It was the moment when the essence of the most lazy sword, The Imperial Sword Form, unfolded itself using the signboard of a hostile sect.

Crack! The sensation of bones shattering.

The warrior's course changed dramatically to Qing's right, where he struck a hapless companion with his own dao.

But regardless of that.

Apathetic strokes continued to cut through the air.

Warriors tumbled to the ground without fail.

They were not dead, but either would die or remain permanently crippled.

After all, what kind of skill would those disciples, who were just having group training, possess?

Moreover, after some time, Kyeon Pohee also returned, backing up Qing.

Thus, what filled the training grounds was blood and tears.

"Stop! Stop it!"

Someone shouted again.

It was a profound voice that carried a noticeable amount of Inner Qi.

But why were the words spoken by those villains all the same?

Qing turned her head askew and gazed at the newly appeared Master.

It was to see if she would hear anything worth listening to.

As her face was covered by a veil, except for her eyes, it seemed the Master thought their gazes met. As such, he politely performed a Clasped Hand Salute.

"Although I do not know which senior you are, please calm your anger."

"So, you want to talk with words? When you have good swords with you?"

The chief instructor Bi Seongnak was sweating bullets at Qing's oblique tone.

The training ground had already become a living hell, filled with groans and cries of pain, but surprisingly, no one had actually died.

Although it was easy to kill, to cripple and neutralize them without killing was a far more difficult task.

Moreover, to face not one but two Masters who remained so calm even after beating up all of their disciples…

Bi Seongnak carefully chose his words.

But what could a member of an Unorthodox group say?

Sadly, it was nothing more than a typical threat.

"Our Bang is under the protection of the Unorthodox Alliance."

Qing snorted.

"So what? Does that oh so great Unorthodox Alliance protect you? Why not just call on your ancestors instead. Where is that Unorthodox Alliance now anyway?"

The Unorthodox Alliance was far, and Qing was near.

Bi Seongnak realized that the authority of the Unorthodox Alliance did not work at all and immediately changed his tone.

"It is not that. I was wondering if we perhaps committed some impropriety against you."

"You don't know who I am? I'm the Earthwork Fairy. You know, today several construction workers, including woodworkers, died. Are you saying you still don't know what impropriety you've committed?"

"What you are saying has no connection to us at all-"

"I already know everything, so don't waste my time with your futile lies."

Bi Seongnak's heart sank.

Although there was a Bang Chief, he was more of a representative than an owner, so there were many bosses who issued commands.

One of them must have started this.

As Bi Seongnak explained the situation, it almost sounded like a plea.

"So we will find the head who started this and hand him over to you. Please, quell your anger."

"A mosquito bit me."

Qing suddenly spoke out of nowhere.

While Bi Seongnak looked puzzled, Qing calmly followed up.

"Should I only find and kill the specific mosquito that bit me? Or should I just crush every mosquito I see?"

Bi Seongnak's expression stiffened.

At that, Qing casually gestured with her hand.

"Alright. I'll give you three moves. You better use all your strength."

At that, Bi Seongnak quietly drew his dao.

Woom. The Sword Force emitted from the blade, it had the presence of a serious and weighty aura, befitting someone who was in the early stages of the Transcendent Realm.

Since Qing had already expressed her intention, what remained was only the clash between martial arts.

Bi Seongnak looked back at the martial arts he had cultivated over a long time, at his Movements.

Was it because it was a challenge at the brink of life and death?

The form of the Dao, which had been vaguely visible in the past, was suddenly appearing clearly in his mind.

Bi Seongnak's heart thumped.

He had the belief that if he overcame this crisis, he would leap forward, ascending a step higher.

And thus, Bi Seongnak clung onto the Dao in his mind.

Then, boom, a force generated from a True Qi imbued step violently trampled down on the ground-

And Qing threw her dagger.

Bi Seongnak flew through the air and slid across the ground with his limbs stretched out.

He flew so powerfully that his hand almost touched Qing's foot.

Qing quickly moved her foot away as if an undesirable object had floated near.

Then, the dark Demonic Qi of the Heavenly Demon Army Corps Step rose up from the Yongcheon Point of her foot, and thud, she stepped on Bi Seongnak's elbow and crushed it.

"Gyaaaak! Guwaaaaaak!"

Two screams echoed.

It was because Kyeon Pohee had stepped fiercely on Bi Seongnak's remaining arm.

"Ack, th-that's not fair… You said you'd give me three moves."

"I don't talk with bugs."

Qing's instep filled Bi Seongnak's vision.

Disposing of a bug nest was easier than she had thought.

Perhaps because of this, her rage still lingered. She didn't feel any joy even after beating and smashing, crushing and tearing with all she had.

Why did they let so many innocent people die before dealing with this simple task?

There was already a large crowd of onlookers gathered in front of the Gwangju Seonbang's door.

The sounds of screams echoed continuously from beyond the walls, and there were more than a few of the Gwangju Seonbang warriors who were fleeing, their faces pale. As such, they couldn't dare to go through the gate as they simply clustered in front of it.

So, when Qing appeared, kicking the dilapidated door and knocking it down, cries of ‘Ooooh' resounded from the crowd.

However, perhaps they were afraid of Kyeon Pohee beside Qing, as they didn't dare to approach her, despite their bright expressions.

After all, Kyeon Pohee was tightly gripping a man's hair.

It was Bi Seongnak, whose limbs were mangled and dangled like a dead octopus.

Even though they did not come near, perhaps they were happy to see her safe, as someone called out and asked Qing about her well-being.

"Fairy! You're safe!"

At that, Qing snickered, showing a smile for the irst time today.

However, despite her smile, she was scolding them in a displeased tone.

"What are you doing, gathering like this as if there's some spectacle to see?"

Qing said this and threw the signboard to the side.

The Gwangju Seonbang signboard, stained with blood, landed with a thud onto the wooden floor of the central dock.

"Whether you burn it or throw it away is up to you. There are no one left unharmed in there, so take whatever looks like it might make you a buck."

At that, the crowd rushed inside the Gwangju Seonbang in a long line.

Their immediate intention was probably to earn a profit.

But in the first place, wasn't that how those Unorthodox bastards lived? By selling ill-will for money?

If they saw trash scattered on the floor, it must have crossed their mind to get their own back.

Qing stared blankly at such a sight before turning her gaze to Bi Seongnak.

"Don't you feel wronged by yourself turning into a cripple? Isn't it sad that you're spending your life as a cripple because you were merely a pawn controlled by those who gave the orders. Ah, that's right. It must be sad to be a hunting dog who just had the bad luck of having a bad master."

Qing snickered before continuing her words.

"So, we should go deal with those who ordered you. Ah, right. If you still have any loyalty left, you can just remain silent. What difficulty is there in guiding the way? Why would I keep someone alive who wants to die? So, what's your answer? Where should we go? If possible, tell me a place that's nearby and doesn't waste any travel time."

At that, Bi Seongnak's expression twisted.

Regardless, he obediently provided an answer.

"To the west of here, there is the Daeseonbang of Haegung."

Qing reached out her hand to Bi Seongnak and spread her palm wide open.

Kyeon Pohee gripped his hair and moved his face to a perfect position for a hit, so Qing gently tapped him on the cheek in satisfaction.

"Good choice. Even if your limbs are crippled, the living still have to live."