\chapter{If You Want to Kill Someone, Prepare Two Graves (9)}

"Nari, it's all a misunderstanding! I didn't drive them out; I just hoped those foolish ones would realize filial piety, and though it may not have been my intention, how can I atone for the sin of driving my father to death, violating the natural order? Therefore, while mourning my father, I wished for them to come to understand their wrongs by living as beggars. How could I possibly have forced my stepson's children to die?"

As the general manager spoke desperate words while glancing to one side, it was none other than the chief judge of Jinping County, overseeing the judgment in the district.

The chief judge cleared his throat and said,

"Esteemed one. That person's words hold some merit, don't they? When mourning one's father, one should ideally build a small hut beside the grave and live there as an outsider, offering sacrifices morning and evening. They should wear uncomfortable mourning clothing that clings to their skin and avoid rich food, keeping unsavory scents at bay to ensure they can't eat to their fill. Compared to that, living outside and begging could be seen as caring for the young nephews, don't you think?"

For reference, the small hut mentioned beside the grave meant there should be no floor or pillars, just thatched together with straw.

It was a dwelling so low that one would have to crawl in and out at head height.

In reality, properly observing the three-year mourning period was much tougher than living as a beggar. Surviving the harshness of the mountains alone while dealing with various predators was a challenge.

The three-year mourning period was that difficult.

No wonder Yuan Shao had once conducted a three-year mourning for both his father and mother; people hailed him as a hero of the realm.

Meanwhile, the historian Chen, who wrote the Records of the Three Kingdoms, had managed to concoct a medicine during his three-year mourning period, just to save himself from suffering, and was thus treated as a lowlife, getting dismissed for approximately ten years.

So, it could be argued that driving someone to a beggar's life was indeed far more merciful than the three-year mourning.

Qing furrowed her brow.

\textit{Who even does three-years mourning?}

The three-years mourning was a political event equivalent to being named the greatest filial child in the world.

To properly observe it was akin to a near-suicidal act; had everyone done so, the entire populace of Zhongyuan might have perished, likely leaving all to rot beside their parents' graves.

"Esteemed one, isn't filial piety the foundation of the country and the most basic duty of a person? Even if Jong's children didn't mean to, they drove their father to his death, so surely, they must face the consequences of that sin. According to the law, it could be said that this person has granted immense virtue to Jong's children."

The magistrate felt a chill run down his spine.

\textit{Somehow, gold had come to light, meaning that this bastard had pocketed the money and sent the rest away!}

And behind him echoed a hushed remark, meant to be heard only at his position, with a most astonishing tone.

- What? Since when did such laws exist in our country? If a child is young and pitiful, should they live as beggars for three years instead of mourning? Is my knowledge of the law so lacking? I must consult someone well-versed in the law.

"Gah! Where exactly is it written that such laws exist!? You! You! Absolutely do not think so!"

The Magistrate was frothing at the mouth.

If the Inspector asked someone knowledgeable in the law, that would mean this incident would flow directly to the royal court.

Erasing family was one thing; it wouldn't be unusual for all relatives, in-laws, even distant cousins and their children to lose their heads.

"E-esteemed one?"

"And how dare you fools even mention the three-year mourning? Then what of Jong's wife? Why is she here and not mourning for three years?"

That's right.

The three-years mourning applied not only to the children but also to the wife.

"Well, since there are no longer elders in the family, this young girl must manage the household…"

"And you! If you're Jong's sworn brother, why are you not mourning for three years?"

"B-because the men in the family were gone, so I'm trying to protect my sister-in-law's business…"

The head manager desperately glanced back at the chief judge.

The judge looked slightly suspicious at the magistrate.

The magistrate, usually indifferent and ignoring the concerns of the common people, was strangely fervent today.

"Esteemed one, their words hold weight. If their business flourishes, it will certainly return the favor for the district's prosperity in the future, aiding the nation's affairs—"

"Gaaaah!!! What nonsense!"

The magistrate interrupted the judge, frothing at the mouth.

Indeed, what the judge said suggested that he would later receive a very generous gift if he showed some consideration.

To the magistrate, that meant nothing but the blade approaching his own throat.

"Who do you think you're killing? Get that man, kneel him down immediately!"

"Esteemed one? E-esteemed one?"

"Quickly! Right away! Gaaaah! What are you doing?"

Beside the head manager and Lady Lee, the judge was forced to kneel.

The head manager exchanged glances with the judge.

'What in the world is happening?'

'I don't know. Did that guy eat something wrong?'

"Haah, haah."

As the magistrate panted heavily, whispers floated back to his ears.

- Now that I think about it, isn't the very death of Jong strange? How could a grown man suddenly die of illness one day? Should we not inquire further from the physician?

"Summon the physician who determined Jong's cause of death immediately! I must investigate the circumstances surrounding Jong's death!"

The head manager's and Lady Lee's faces drained of color.

Be that as it may, moments later, a physician was dragged into the estate, hanging limply between two soldiers.

It wasn't even noon time yet.

A sudden assault by countless soldiers.

The harsh transportation of a criminal.

All the troops of the district crowded into the plaza, overwhelming the space.

And among them, the head manager and Lady Lee were on their knees.

Anyone could see this was a situation gone awry.

Thus, the physician immediately bowed his head.

"I have committed a grave sin! I could not withstand the threats! The… the head manager coerced me!"

"W-what! No! It wasn't me! That person is a fraud, pure nonsense!"

The head manager exclaimed in shock.

In truth, the physician hadn't said anything yet, merely making an intense confession.

"Shut that fool's mouth!"

"Wait, eh! Ugh!"

The constables rushed over to gag the head manager.

"Did you really say you were threatened? What sort of threat?"

"Ugh, ugh!!"

"Uh, they asked me to change the cause of death. Originally, the deceased died of strangulation, but they told me to say it was sudden death due to a disease…"

The atmosphere fell silent.

Even the judge, also kneeling beside him, stared at the head manager, just as bewildered. So, how surprised must the others must have been?

\textit{Hmm. Somehow. I had a feeling this would happen, but maybe I should've left the kids behind…}

Qingg examined the complexions of the Jong brothers.

Fortunately, the little one didn't know what's going on and just stare blankly in boredom.

However, the older one already had a deep hatred on his face and his fists were clenched and trembling.

Qing put her hand over the fist.

"Are you okay?"

"I. I want to hear what that, ugh, Uncle, no, that man has to say. Did he really killed my father? And if so, why? Was it simply a vile greed? Was all the kindness he'd always shown us, his nephews, a lie?"

Cheong looked at the magistrate.

The magistrate, who was quick-witted, was one step ahead.

"I will give the sinner a chance to confess his crimes. How could you commit such a heinous act? Why is the cause of death of the Jong clan hidden? And who is the villain?"

Qing smiled bitterly.

\textit{Even if you ask now, you'll probably get an obvious answer.}

\textit{I didn't do it, it's a false accusation, I'm innocent, it's unfair, etc.}

\textit{Well, the guy who coveted his sworn brother's wife and swallow up the family fortune is about to reveal that he had such answers.}

But, what was the head manager's answer?

“……I did it on my own.”

“Dage!”

Ms. Lee called the head manager as if screaming.

The head manager sighed at that.

"Estemed one. I was simply doing what I had to do. Mr. Jong, the merchant, may pretended to be a good person, but he's actually a beast of burden, a scumbag who deserves to die."

\textit{Whoa, this is something I didn't expect at all.}

“What does that mean?”

"It's exactly as I say, Esteemed One. Mr. Jong, the merchant, was such a vicious man, a beast of a man, so cruel that he couldn't even be considered human. He beat his wife to death in the past, and now he was trying to kill his remaining wife, too."

“Dage!”

"I killed the beast and saved his wife. That's all. Furthermore, I attempted to eliminate the offspring of the beast that inherited its blood. Mr. Jong's father was also a descendant of that species, for I judged it to be the beast's nature, passed down through blood."

“…What?”

The magistrate was silent.

Not only the magistrate, but everyone fel silent.

Even Qing fell silent.

There are times when a voice just doesn't sound fake, and that voice right now is one of them.

A voice filled with deep resignation, a voice that felt empty and hollow, as if everything had been given up.

Of course, if you are a great conman, you can fabricate even this.

To Qing, the greatest of con artists, the greatest con artist in the world, who knows how to cheat without lying, this didn't sound like a lie.

Suddenly, the young boy, Jong Mun-woon, burst forth with a roar.

Without hesitation, he grabbed the head manager by the collar and unleashed his fury.

"That's a lie, a lie! It's a lie! You, you were trying to sleep with that lady, so that's why you're saying such lies!"

But the head manager merely smirked.

"Of course, a beast wouldn't love its offspring. Nephew, you won't understand. But isn't it odd? There were dozens of servants in this estate; has any of them ever shown you kindness? Or have you ever thought that was strange?"

"That's because you told them to—"

"Do you truly believe that?"

Suddenly, Jong Mun-woon glanced around.

Familiar faces among the onlookers, their gazes—whether pitying, indifference, or contempt—crossed his sight.

Yet, among them, none bore a look of denial.

The head manager calmly regarded the magistrate.

"Esteemed one. If you dig beneath the trees in the estate, you'll find dozens of unmarked skeletons. I stood watch and silenced them; I am indeed guilty of complicity in the matter. However…"

In that instant, desperation glimmered in the head manager's eyes.

"This lady has done no wrong. She was merely a poor woman who was nearly killed by her own husband, and I wish for her to have your mercy."

"Dage…"

Lady Lee's tears began to flow.

But behind her, the judge was sweating profusely, his eyes darting about, with the atmosphere becoming utterly fraught.

The magistrate's eyes also flitted back and forth.

\textit{What should I do about this?}
