\chapter{If You Want to Kill Someone, Prepare Two Graves (7)}

This time, by some twist of fate, I ended up playing the role of an elder martial artist, making it awkward to suddenly switch to a lighter, more casual demeanor.

The reason Qing acts like a vulgar, unreasonable person whenever she engages in slaughter isn't because of her inherent nature. (Probably.)

It's just because it pisses people off more.

Imagine a solemn martial artist executing a villain.

In response to the villain's desperate cries—"Why were you doing this? Doesn't everyone live like this?"—the martial artist would calmly reply with a single word, "Justice."

And then, without hesitation, turn and walk away.

So cool. Truly cool.

But doing it this way inadvertently elevates the villain's status.

Being executed by a legendary martial artist from stories adds to their prestige, making them seem more tragic and profound.

Now, imagine a villain being executed by someone who's utterly shameless, lacks any sense of gravitas, and spews nothing but vulgar, filthy words.

It doesn't feel like an execution at all.

It just feels like they had the bad luck to run into a lunatic.

The onlookers would just laugh and say, "Serves them right. They lived dirty, so of course they died dirty."

Their death—or crippling—becomes nothing more than a joke.

For this, Qing can throw away her dignity without a second thought.

The greatest slaughter genius in history, one who even mocks death itself!

But now, having accidentally taken on the role of an elder, it would be weird to suddenly break character.

If the persona collapses, so does everything that came before.

After going through the trouble of blocking the Five Poison Sect's involvement, people might start wondering, "Wait, were those fake Five Poison Sect members actually real?"

So Qing strides forward with deliberate, dignified steps, exuding an air of authority.

Behind her, the sound of the crowd following—wait, was it even allowed for spectators to enter someone else's estate?

Past the main gate, the open courtyard of the trading company's estate unfolds.

And there, lined up with clubs in hand, were all the estate's laborers.

Though their faces were pale, their expressions far from confident.

After all, no matter how strong they are, laborers were no match for a martial artist armed with a sword.

They've come out because, as employees, they have no choice—but if it comes down to a fight, they'll flee without hesitation.

A somewhat disappointing confrontation.

\textit{Hmm, I thought there'd at least be one wandering martial artist standing in the way.}

\textit{Did they really think two Blood Cult members disguised as Five Poison Sect disciples would be enough?}

Of course, most martial artists wouldn't want to antagonize a major sect like the Five Poison Sect.

But a group of laborers with clubs isn't exactly a formidable force.

To a skilled swordsman capable of emitting sword qi, they're no threat at all.

But to a third-rate martial artist, they'd be a life-or-death challenge.

And depending on their numbers, they could even pose a threat to a second-rate martial artist.

Especially if that martial artist was just a young boy.

A boy who's small for his age, stunted, and who's spent the last month being hated by everyone for reasons he doesn't even understand.

Jong Mun-woon's hands tremble.

These were the same servants who used to smile and call him "young master," but now they glare at him with open hostility.

He doesn't want to face them.

He doesn't want to see the people he once lived with now despising him.

He's only sixteen—legally an adult in Zhongyuan, but still just a child.

No, even an adult would struggle.

The weight of undeserved hatred was unbearable, no matter how old you are.

Jong Mun-woon stares at the ground.

The reason he tried to dissuade his benefactor wasn't just out of concern for her—it was because he wanted her to take him and his brother somewhere else.

He didn't want to face this.

He'd imagined—even fantasized—about asking her to take them in and teach them martial arts, but he never dared to hope for it.

Just getting to his mother's hometown would've been a lifelong debt of gratitude.

Then, in that moment—

A hand as smooth as silk—no, far softer—slid into his grasp, fingers intertwining with his and squeezing firmly.

Though the touch was cool, the warmth in its meaning was unmistakable: "I'm on your side."

Yes, on his side.

Jong Mun-woon looked up at Qing.

For a woman, she was quite tall.

Though her face was hidden behind the veil, he could imagine her smiling kindly down at him.

Then came her voice:

"How strange. Since when do servants greet their master with clubs? What kind of absurdity was this?"

In an instant, Jong Mun-woon's expression shifted.

"The master of the estate entering his own estate."

That's right. The master. The Jong Trading Company was his. With his father gone, he was its rightful owner.

What kind of shameful spectacle was this?

Jong Mun-woon lifted his gaze.

The faces of the servants were familiar.

He resented them. He resented them so much he didn't want to see them. But avoiding them would be the childish act of a coward.

More importantly, it would be disrespectful to the benefactor who'd brought him this far.

And now that he faced them, their expressions were pitiful.

Beneath their scowls, fear was plain to see—even to Jong Mun-woon.

And then—

"Shh, it's okay. It's okay."

His benefactor's gentle whisper.

Jong Mun-woon turned his head and saw his younger brother clinging to her waist, face buried in her robes.

Though he'd always doted on his brother, this time, he felt a surge of irritation.

This brat—at a time when he should be standing tall as the master of the estate, he's shamelessly clinging to a young woman, burying his face in her waist like—ugh, this little—

Then, a voice cut through the air:

"Stop right there. You seem to be under a misunderstanding. The master of the estate? How could the ungrateful wretch who killed his own father inherit anything?"

A bold, confident declaration.

Qing's gaze shifted to the man who'd stepped forward from the crowd of servants.

Square jaw, thick eyebrows, piercing eyes, broad shoulders—a thuggish vibe.

Beside him stood a woman with delicate features, dressed in fine silk.

Unlike the servants, these two were clearly the magistrate and the second wife, Lady Lee.

But there's an unwritten rule in Zhongyuan:

Never argue with the Heavenly Demon Sword.

"Well, isn't this rich? The beast who slept with his brother's wife, poisoned him, and before the funeral was even over, framed his nephews and drove them out—what right does he have to speak?"

The brutal insult hung in the air.

The spectators' eyes gleamed with excitement.

Wait, what? Slept with his brother's wife, killed him, and framed his nephews?

What kind of monster does that?

Their gazes turned to the magistrate.

A mix of contempt and anticipation—or maybe more like half-contempt, a quarter-anticipation.

Of course, the part about poisoning was entirely made up by Qing.

Because it made him sound even worse.

But the magistrate and Lady Lee felt their hearts drop.

Their eyes met in silent panic.

How? How does she know?

Did you—did you tell someone?

Or did the physician talk?

"Th-that's slander! Where's your proof?"

"Where were secrets kept in this world? We'll find it soon enough."

"Such nonsense—ahem. Look, Great Hero, this is the situation."

A man with a large saber stepped forward from the servants, blocking Qing's path.

"I am Yi Jin-byeong, the Great Saber of Yiyang."

\textit{Great Saber of Yiyang?}

By the naming conventions of Wulin, 'Yiyang' was a place name, and 'Great Saber' meant he wielded a large blade.

Not an exceptional title.

\textit{But Yiyang? The Yiyang I know? If it's Yiyang in Hunan, that's a major city.}

This was the general manager's second contingency.

Luckily, a merchant he did business with had a hired martial artist—a renowned expert from Yiyang—whom he'd paid two chests of gold to bring here.

If treated well, he might stay. Or at least stick around until the child came of age.

Qing studied the swordsman.

And the number above his head.

\textit{Hmm, someone with 'Yiyang' in their title isn't weak. His karma suggests he's not some fugitive hiding in the boonies.}

\textit{So why is a decent martial artist working for a lowlife in this backwater?}

Qing paused in patting Jong Mun-yeok's head and flicked her wrist.

A brief, almost imperceptible flash of red light—like a passing illusion.

Only a novice wouldn't recognize it. A titled martial artist would know.

The Great Saber's expression froze.

"Yiya's Great Saber, hmm. You mean Yiyang in Hunan?"

"Yes."

"Really? I think I heard about you from Wang Ga-sang of the Wang Trading Company. You're friends with him, right? Even if it's a distant connection, we're practically family. How about stepping aside?"

The Great Saber let out a sigh.

"That sword—now I see. You must be the elder Wang Hyung always said he owed his life to. Since you're his benefactor, you're mine as well. I dare not raise my blade against you. I'll take my leave."

He bowed.

But here's the thing: in Zhongyuan, out of ten people, two were named Wang, two were named Yi, and another two were named Jang.

So "Wang Ga-sang" could refer to any number of people.

In short, their exchange boiled down to:

'Leave now if you know what's good for you.'

'…Thank you.'

As he turned to go, the Great Saber glanced back.

He had to say something.

Not to Qing, but to the general manager.

He sent a telepathic message:

'You should've known your limits. Two chests of gold to send me to my death? Normally, I'd hold a grudge, but given the circumstances, consider the gold my payment.'

No refunds.

The magistrate's face turned ashen.

Qing smirked.

First, the Blood Cult's reinforcements.

Then, the hired swordsman.

What's next?

Suddenly, the general manager dropped to his knees.

"G-Great Expert, there's been a misunderstanding! I can explain everything!"

Kneeling meant he was out of options.

"A misunderstanding?"

"Yes! First, about those boys—my nephews. How could I, their uncle, be so heartless as to cast them out? I just wanted them to suffer a bit before taking them back. Truly! I planned to call them back after the forty-nine-day mourning period. The idea that I coveted the estate was a complete misunderstanding!"

"Hmm. Is that so?"

"Yes, truly! I've already discussed it with the late master's people. Isn't that right?"

The general manager turned to the servants.

They murmured in agreement.

Lady Lee chimed in:

"Elder, I'm carrying his child. How could I—how could I do such a vile thing with another man, especially his sworn brother? I just—*sob*—after he passed, I didn't know how to manage the estate, so I sought advice—*sob*—"

She broke down crying.

But Qing's brow furrowed deeply.

\textit{Oh, please. Who do you think you're fooling?}

This was the most convincing tearful performance, designed to evoke pity—a terrifying, invisible poison.

The infamous "Ten Thousand Flowers Blooming" technique.

A signature move of Tang Lan-Ah, the Saintess of Tears.

Having witnessed it countless times, Qing wasn't fooled by such amateurish acting.

But the crowd's contempt had faded, replaced by doubt.

Wait, whose side was telling the truth?

Qing paused, considering.

\textit{Hmm, how should I deal with these two?}

\textit{How can I make sure word spreads that they got what they deserved?}

As she pondered, a new voice rang out:

"Halt! How dare you cause such a disturbance in broad daylight, under the majesty of the law!"

A third party had arrived.

All heads turned toward the estate gate, where a group of men marched in.

The characters "捕" (arrest) and "衙" (office) emblazoned on their chests marked them as constables.

\textit{Ah. So they took bribes too.}

Not surprising, of course.

In Zhongyuan, no merchant operates without bribing officials.

It's basic common sense.

If you want to do business here, you have to pay off the authorities.

As Qing observed the constables and their batons, the general manager's voice rose triumphantly:

"Constable Jang! Over here! Glad you could make it! It's nothing serious, but your presence is much appreciated! Hahahaha!"

Constable Jang was their leader.

And his loud proclamation made it clear: "This constable and I are close friends."