\chapter{If You Want to Kill Someone, Prepare Two Graves (8)}

However, the expression on the head constable's face was far from bright.

Though he had rushed over because it was his duty to follow orders, confronting a martial artist was something anyone would hesitate to do.

Originally, there was an unspoken rule of 'official and martial non-interference'—no matter how bloody the conflict, the authorities would turn a blind eye.

In return, martial artists would step back and yield when the authorities intervened.

It was a mutual understanding, a form of respect between the two sides.

But it wasn't always like that.

When even ordinary citizens of Zhongyuan were driven to desperation, they would kill and flee far away. So what about martial artists, who were even better at killing and escaping?

If things went south, they could just cut everyone down and vanish.

Some might hold grudges.

If you made an enemy of a martial artist, who knew what kind of retaliation might come later?

What if they came back later and drew their sword?

There were already horror stories circulating about constables who had met gruesome ends because of this.

But what could be done?

It was the constable's job to follow orders. If he quit on the spot, what would happen to his family?

So, swallowing his curses, he thought, '\textit{Damn it, the higher-ups pocket the bribes while the lower ranks take all the risks. What a filthy world.}'

Of course, the head constable himself wasn't innocent either, someone in his position had considerable power in the constabulary.

For these reasons, the head constable wasn't thrilled about the general manager's friendly overtures.

And then there were the corpses of the Five Poison Sect disciples piled at the entrance.

Of course, corpses were nothing unusual to the people of Zhongyuan, so it wasn't particularly shocking.

But these were Five Poison Sect disciples.

Either the martial artist was stronger than the Five Poison Sect, or they weren't afraid of the sect.

Either way, this was no opponent for a mere head constable.

Thus, the head constable's expression twisted into something sly and servile, his voice trembling thinly.

"Ah, well, my lord—no, esteemed one—why, um, why are you causing such a, uh, disturbance? There are procedures and laws for these things, you see? If you have any grievances, you should first report them to the authorities…"

His careful, non-confrontational tone drew a single thought from the onlookers:

'He's scared.' 'Of course he is.'

No one had expected the head constable to come in roaring and shouting.

That would've been absurd.

In fact, this scene was just another infamous tale among constables—a rookie, full of enthusiasm, yelling at a martial artist about the majesty of the law, only to meet a gruesome end.

Similar to the stories in Qing's homeland about, 'Are you the supply officer?', well-known but unverified tales.

So the crowd was just curious how this fierce martial artist would react.

Would she explode in anger over the suspicions surrounding the Jong Trading Company?

Or would she draw her sword?

Unfortunately, neither happened.

"Hmm, you there. Come here for a moment."

Qing wiggled her index finger back and forth.

The head constable's pride might've been wounded, but his heart sank even further at the casual, almost dismissive tone.

"M-me? Why…?"

"Yes, you. I'm not going to harm you. I just have something to say."

The head constable hesitantly approached.

"Closer. No one's going to eat you. Just lend me your ear."

"Y-yes…"

Qing leaned in, her veil brushing his ear, and whispered:

"Go tell the magistrate of this district to come here immediately. If he doesn't, he'll regret it for the rest of his miserable life. It'd be best if he hurries."

The head constable's face turned deathly pale.

"I, uh—"

"Go on. I'm saying this for your own good. Deliver the message as quickly as possible. Seriously."

"But—"

The magistrate was the highest authority in the district.

A mere head constable couldn't even look him in the eye, let alone deliver such a message.

"You're not going? I'm warning you for your sake. If I go, you'll be in big trouble."

She meant it.

If a lowly head constable delivered the message, the magistrate might be offended, but he'd eventually understand.

But if Qing went herself?

The head constable wouldn't keep his position for long.

"Gah!"

With that, the head constable sprinted away, leaving only his shouted orders behind.

"You lot, guard the scene! I'll be back soon! Don't let even an ant escape!"

The crowd's expressions filled with confusion.

But there was no need to explain. Qing casually took the hands of the two boys and strolled forward.

The servants panicked, scrambling aside, while the magistrate shouted.

"S-stop her! Why aren't you doing anything? Stop her now!"

The constables remained dutifully still.

The head constable had told them to guard the scene, not to block anyone from entering.

They just had to stand there.

Qing walked step by step.

The general manager retreated step by step.

Finally, face to face, she said one word:

"Move."

"What?"

"I said move."

The general manager stumbled back.

Qing walked past him.

In a merchant's estate, the main building was usually straight ahead from the gate, with the merchant's office and reception hall at the center.

Sure enough, the door was open, revealing luxurious chairs arranged neatly on either side of the main seat.

Qing released Jong Mun-woon's hand and pointed to the empty main seat.

"Go on. Sit there."

"Huh? How could I—you should take the main seat, Benefactor—"

"What nonsense? The master sits in the master's seat. Since when does a guest take the main seat?"

It was common sense in Zhongyuan.

The host always took the main seat.

The only exception was if the host was serving a higher authority—in which case, that authority became the true host.

But Jong Mun-woon seemed to be realizing this basic truth for the first time.

\textit{My seat. The master sits in the master's seat.}

That's right.

His father's seat. And now, after his father's passing, this seat was his.

Jong Mun-woon carefully lowered himself into the seat of the trading company's master.

As if performing a ritual, he moved cautiously.

\textit{My seat. My place. What I should've inherited. My rightful—}

"Hey, kid, sit next to your brother."

"I want to stay here…"

In an instant, Jong Mun-woon's eyebrow twitched.

His younger brother was shamelessly perched on the Benefactor's lap.

Just as some emotion—resolve, perhaps—was about to well up inside him, it vanished.

Instead, something like irritation bubbled up.

But what could he say?

Jong Mun-woon was sixteen.

Wouldn't it be pathetic to envy his eight-year-old brother in front of the Benefactor?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The magistrate of Jinping County couldn't believe his ears.

A mere head constable had barged into his residence, spouting unbelievable nonsense.

"What?"

"Th-the martial artist said you must come immediately, or she'll make you regret it for the rest of your life…"

The message, originally delivered with consideration, had morphed into an outright threat.

"Ha! How dare some martial artist from the underworld order around an official entrusted by the Emperor! The law is absolute!"

Naturally, the magistrate was furious.

At his level, he didn't fear martial artists much. (Of course, anyone wielding a sword was intimidating.)

After all, if a martial artist targeted a high-ranking official like him, the state wouldn't stand idly by.

"Men! Summon the patrol captain and the prison warden—no, mobilize all the troops! I'll see this wretch's face for myself!"

The patrol captain and prison warden were titles.

The patrol captain oversaw public order, while the prison warden managed the jail and its guards.

Thus, the enraged magistrate set out.

Not out of fear of the martial artist's warning.

But because he couldn't let such disrespect slide.

If he went personally, he could later charge her with a crime.

So he mobilized every available soldier, forming a grand procession.

Their destination: the Jong Trading Company.

As the magistrate rode in his palanquin, his anger grew with every thought.

The official procession included drummers and trumpeters, creating a deafening uproar.

The spectacle drew even more onlookers, curious about the commotion.

"The magistrate has arrived!"

After a brief commotion to clear the corpses at the entrance, a loud voice announced the magistrate's arrival in the estate's courtyard.

Everyone bowed their heads—including the general manager and Lady Lee.

For a district magistrate, a bow was sufficient.

But even that was a display of immense authority.

"Magistrate! In our darkest hour, your presence moves me beyond words—"

"Silence! Where is that person? What does she intend to do now?"

All eyes turned toward the open room at the center of the main building.

The magistrate's veins bulged.

What? She's not even waiting outside?

How dare she summon him with threats and then ignore him!

Disrespecting him was tantamount to disrespecting the Emperor!

Such insolence!

The magistrate stormed forward.

The moment he entered the office, the veiled woman turned her head slightly and spoke.

"Ah, the magistrate? Please take a seat. I have something confidential to discuss. Mun-yeok, go sit with your brother for now."

The boy on her lap scurried to the main seat, plopping down beside his brother.

At least the boy in the main seat had some manners, bowing awkwardly despite his discomfort.

By now, the magistrate was burning with curiosity.

He sat beside Qing, leaning back in his chair.

A whisper reached his ear.

-I forgot my identification badge, so I can't prove it now. But if you insist, you can send a messenger to the Kunming Prefect and ask if a veiled woman with a large sword showed an inspector's badge.

In that instant, the magistrate jolted in his seat.

His back straightened instantly, his hands resting respectfully on his knees.

His insides turned to ice, and his heart pounded wildly.

\textit{An imperial inspector!}

"N-no! How could I doubt you?!"

Even if it was a fake, one must never question an imperial inspector.

Suspecting a fake wasn't a crime—after all, impersonators were executed along with their entire families. Bowing to one wasn't a big deal.

But doubting a real inspector?

That would doom his entire family.

"But Magistrate, I've encountered a shocking incident in Jinping—the matter of the Jong Trading Company."

Here, 'I"' referred not to a young girl but to a woman of low status.

Meaning the inspector didn't want her identity revealed.

"After the merchant Jong's sudden death, his sworn brother and stepmother conspired to drive out his sons. Doesn't that sound highly irregular? Do you know anything about this?"

Sweat dripped from the magistrate's chin.

Now that he thought about it, hadn't the Jong Trading Company sent him a chest of gold not too long ago?

Of course, someone of his rank didn't bother with such trivial details.

Bribes were skimmed at every level, with only the largest sums reaching him.

He'd just acknowledged the "gesture" and moved on.

But now, he erased that memory.

\textit{I know nothing about this.}

\textit{Maybe some nameless commoner, moved by my governance, donated their wealth?}

\textit{Yes, that happened sometimes to capable officials.}

\textit{Though I should've refused and returned it.}

With his memory 'cleared', the inspector's words were nothing short of shocking!

"Heavens! Such a heinous crime! Unforgivable!"

The magistrate sprang to his feet and marched to the doorway.

"Men! Arrest Jong's sworn brother and stepmother at once!"

With the troops he'd brought, the constables swarmed in and forced the two to their knees.

"Ack!"

"Magistrate! There's been a misunderstanding!"

"Silence! How dare you call yourselves human? You beasts! I'll have your heads—"

"Ah, Magistrate. Shouldn't we hear their side? Justice must be impartial. They might be innocent."

"—but we can't treat them as criminals yet. I'll hear your explanation. Why did you drive out Jong's sons?"

The magistrate smoothly changed his tune.

Qing leaned back in her chair.

\textit{Huh, so this is the taste of power?}

\textit{I wasn't planning to play inspector, but this is… surprisingly addictive.}

\textit{I shouldn't get hooked.}