\chapter{If You Want to Kill Someone, Prepare Two Graves (6)}

What Zhongyuan people love most was gold.

Their second favorite thing was watching fights.

So imagine their feelings when they heard vivid accounts from eyewitnesses about a female martial artist cutting off the arm of a beggar gang leader in one stroke to save two plague-ridden kids.

The residents of Jinping County were especially devastated.

'Why, oh why, wasn't I there to see it myself?!'

'The world was truly unfair!'

Jinping was a remote backwater, a frontier within a frontier, where few travelers passed through except for merchants.

And with the Five Poison Sect maintaining a tight grip for so long, even disturbances were rare in this peaceful town.

Watching martial artists wield their blades was a spectacle one might be lucky to see once a year.

To miss such a show happening right in their own city—how heartbreaking and frustrating!

But such regrets were short-lived.

'Wait. She saved plague-ridden kids?'

'You think she'd just stop at saving them?'

'Exactly! Right! She's going to storm the Jong family's trading company, isn't she?'

And with that, the commoners of Jinping County exchanged glances and, without needing to say a word, sprang to their feet.

The same scene played out simultaneously across the city.

Before anyone knew it, a crowd had gathered in front of the Honghagak Inn, the finest in Jinping, murmuring among themselves.

'Is it true that the martial artist is here?'

'I asked the waiter, Jeong, and he said it's real.'

'She's going to storm the Jong family's trading company? But when?'

'How should I know? Could be today, could be tomorrow—it's up to the martial artist, isn't it?'

'I hope she comes out soon. I noticed a leak in the rice paddy, but I can't be bothered to fix it now…'

No one knew when the martial artist would make her move, but they were determined to wait however long it took.

Some were even willing to abandon their farming duties just to witness a single sword fight.

If the martial artist didn't act soon, many would face serious difficulties with the spring planting.

Fortunately, the martial artist—Qing—appeared quickly.

For this alone, Qing could be credited with saving a third of Jinping's farming season (Jinping practiced triple-cropping).

"Ooh, she's here."

"A female martial artist with a big sword, just as they said."

Qing was slightly taken aback.

An unexpected crowd had gathered outside the inn. What was this about?

"Eek!"

The younger beggar, Jong Mun-yeok, startled, clung tightly to Qing's side, burying his face in her robe.

The faint trembling from the child spoke volumes about the hardships he'd endured at the hands of others.

"Shh, it's okay. It's okay."

Qing's eyes turned fierce as she patted Jong Mun-yeok's head.

\textit{Come to think of it, aren't these people all bastards?}

\textit{Surely, they knew something was off about what happened at the Jong family's trading company.}

\textit{But then again, what could they do?}

Silence didn't make them accomplices.

Life wasn't easy for the commoners, and standing up for others when everyone else was turning a blind eye was never simple.

Especially in Zhongyuan, where community bonds were strong.

It took immense courage and strength to defy the crowd and act alone.

Annoying as it was, it wasn't a crime. Being callous wasn't punishable.

Qing had lived in Zhongyuan long enough to understand.

Her initial confusion faded as she quickly grasped the situation.

\textit{Hmm, having an audience might not be so bad.}

\textit{The more witnesses, the harder it would be for anyone to harm the Jong brothers later, using the Bai smallpox as an excuse.}

With that in mind, Qing deliberately raised her voice, adopting the tone of an elder.

"Well, let's go. Lead the way."

Not that they needed guidance.

The crowd had already cleared a path in the direction they were headed.

Following Jong Mun-woon's lead, Qing walked with the people of Jinping trailing behind her like a tide.

And so, to the Jong family's trading company in eastern Jinping!

Not exactly grand, but a moderately large estate. At the main gate stood three martial artists in familiar uniforms, posturing with an air of importance.

The same uniforms Qing had grown sick of seeing in the mountains, the Five Poison Sect's uniforms.

"Benefactor, those are martial artists from the Five Poison Sect. W—we'll be fine. There's no need for you to antagonize the Five Poison Sect for our sake—"

"What a thoughtful thing to say."

Qing ruffled Jong Mun-woon's head.

\textit{Kids are just the right height for head pats.}

\textit{Anyway, hmm, the Five Poison Sect.}

\textit{Why hadn't I thought of them?}

Qing's goal was to monitor the Blood Cult disguised as the Five Poison Sect until either Diancang's reinforcements arrived or Zhuge Lixian's message confirmed their refusal.

If they were up to something suspicious or horrific, she'd stop them. Otherwise, she'd observe. If they fled, she'd track them.

Directly clashing with the Blood Cult disguised as the Five Poison Sect was problematic.

Qing's mind raced.

Her intelligence, which only spiked when she needed to outwit someone, worked overtime. If she had a pretext—and with this crowd—maybe she could remove these imposters without the Blood Cult being able to retaliate.

Qing stopped at an ambiguous distance, leaving the Five Poison Sect imposters at the gate unsure how to react.

If she tried to enter, they could stop her. If she walked past, they'd assume she was just passing by.

But Qing just stood there, patting the heads of the two kids flanking her.

After a moment, Qing finally strode forward.

The Five Poison Sect martial artist cleared his throat and boomed,

"Halt! This estate is under the protection of the Great Five Poison Sect. State your business!"

"Hmm. You claim to be Five Poison Sect disciples?"

Qing grinned beneath her veil.

\textit{Hadn't their leader declared a full-frontal assault, shouting about suicide attack to all Five Poison Sect members? Or something like that.}

\textit{These are Blood Cult members wearing the Five Poison Sect's disguise.}

"But I don't recognize your faces. Which generation are you from? You should greet your elders first."

"Huh?" "What?"

Dumbfounded noises escaped the two.

This was completely unexpected.

"I asked which generation you're from. Whose disciples are you?"

"Uh, well—"

"Why can't you answer? Are you up to something shady?"

The two exchanged glances.

Some silent communication passed between them.

"I'm Jang Seong-hwan of the second generation."

"I'm Kang Ryeom-eon of the second generation. May we ask which esteemed senior you are?"

The crowd's expressions turned slightly disappointed.

This didn't seem like the prelude to a sword fight.

They must have assumed Qing was an older martial artist connected to the Five Poison Sect.

Qing tilted her head beneath her hat.

"Was there someone like that in the second generation? But I don't recognize your faces at all. What's going on here?"

The two visibly panicked.

Qing cheered inwardly.

Just as she thought—Blood Cult members. She'd wondered if the Five Poison Sect had secretly kept a few disciples aside despite their leader's declaration of a full-frontal assault.

But judging by how fiercely those disciples had charged, it seemed unlikely.

"Uh, well, we joined later—"

"Aha! My relationship with him! Was severed! After a big! Fight! We're now! Strangers! So even if I pass by! I wouldn't! Think of stopping by! That's the kind of relationship we have!"

Qing's oddly emphasized shout was deliberate.

If the Blood Cult disguised as the Five Poison Sect got wind of their cover being blown, it'd be trouble.

This was for the crowd's ears.

"This is highly suspicious! How could you induct second-generation disciples while still training third-generation ones?!"

"Uh, our master took us in personally."

It wasn't unheard of for new disciples to skip generations and join higher ranks.

Qing herself had done so.

Becoming Ximen Surin's disciple had instantly elevated her to the same seniority as the Divine Maiden Sect's leader.

But Qing didn't give them time to explain and pressed further.

"Are you really Five Poison Sect disciples? Or are you impersonating them?"

"How dare you! Even if you're an acquaintance of our leader, you have no right to insult us like this!"

"Oh? Really? Then answer me this: What is the name of the fourth elder among the grand elders?"

"Huh?"

"Even if you joined later, you should know the names of your sect's elders. What is his name?"

"Well…"

The two Five Poison Sect imposters exchanged nervous glances.

How would they know the name of the fourth grand elder of another sect? Especially one as obscure as that?

The crowd buzzed with whispers.

They'd been slightly disappointed earlier, but now things were getting interesting.

Could it be that the Jong family, desperate for the Five Poison Sect's help, had hired imposters?

But would they really be that stupid?

"Why can't you answer? Aha! You dare impersonate the Five Poison Sect?!"

The two Five Poison Sect—no, Blood Cult—members panicked.

They'd memorized basic details to pose as Five Poison Sect members, but they couldn't possibly know the names of all the supreme elders.

One of them suddenly dropped to his knees.

"Forgive me! This disciple is too foolish to remember the elder's name!"

\textit{Oh ho. Playing that card, are we?}

\textit{Not bad.}

But Qing wasn't having it.

In arguments, the loudest voice usually wins—and this was a performance for the crowd.

"You never knew it in the first place! Because you're imposters!"

"No! If you contact our sect, you can verify our identities!"

"Nonsense! You're just stalling for time to escape!"

"That's not true! Then come with us to the Five Poison Sect to confirm—"

"Enough! Then answer this: What is the name of the ninth disciple of your generation?"

"Uh…"

The Blood Cult member's eyes darted around.

Of course, he didn't know.

Neither did Qing.

She was just throwing out obscure questions.

"What is the name of the pond in front of the leader's residence? The one named by the leader's grandfather!"

"Uh…"

Qing didn't even know if such a ond existed. Who cared if the leader's grandfather named it?

But any respectable sect would have an artificial pond in their leader's residence.

It was a standard luxury in Zhongyuan architecture.

"What is the name of the dining hall before the current one?"

"Uh…"

"When the leader was young, his mother measured his height against a tree! He later hung a plaque there in her memory! What does it say?!"

"Uh, the Five Poison Sect leader—no, the leader's mother… when did she pass away…?"

"Silence! You don't even know the date of your leader's ancestral rites?!"

If the afterlife existed, the souls of the Five Poison Sect members would be weeping tears of blood.

'Our dining hall has never changed! It's a two-hundred-year-old tradition!'

'And no such tree exists! The leader's mother is still alive and well! She's still healthy!'

The questions grew increasingly absurd.

Things only insiders would know—utterly meaningless to outsiders.

Of course, since the questions had no real answers, the imposters couldn't respond.

But the crowd grew more excited with each question.

'These guys are definitely imposters!'

'No matter how desperate the Jong family is, hiring fake Five Poison Sect members in Five Poison Sect territory? They must be insane!'

"What do you even know? Then, what is the name of the Five Poison Sect's oldest, most traditional restaurant, passed down since the time of the supreme elders?!"

"Uh—"

"You scum! I may have severed ties with the Five Poison Sect, but impersonating them is unforgivable!"

With a thunderous boom, Qing's body shot forward.

The legendary short-distance leap—the Heavenly Demon's Reigning Steps!

A crimson sword light flashed, and the Blood Cult member's head rolled across the ground.

The moment the crowd had been waiting for! A collective "Ooooh!" erupted.

The remaining Blood Cult member, still on his knees, frantically reached into his sleeve and sprang up—

Slick.

The blade pierced his forearm and emerged from the opposite wrist. His body slumped to the ground, diagonally severed.

\textit{Ah, this is the stuff.}

She'd love to savor the fight and flay them a bit, but she needed to shut them up quickly.

Now, the Five Poison Sect couldn't interfere.

With so many witnesses, the Blood Cult couldn't risk exposure by claiming these were real Five Poison Sect members.

After all, they were imposters.

If they insisted these were their disciples, Qing—a real elder—would expose them.

And since she'd publicly declared her severed ties with the Five Poison Sect, they wouldn't dare provoke her further.

Not that they wouldn't hold a grudge.

But what could the Blood Cult do? They were already hated by the entire Zhongyuan.

Having broken through the Five Poison Sect's blockade, Qing strode toward the Jong family's main gate.