\chapter{If You Want to Kill Someone, Prepare Two Graves (2)}

Being a beggar was a pretty good gig.

You don't have to work your whole life, you can sleep when you want to sleep, play when you want to play, although you can't eat when you want to eat.

Well, there's no such thing as a perfect job in this world.

The problem was that even though being a beggar was such a good job, you don't need even the minimum qualifications to become one.

It was open to anyone, and anyone could become a beggar right away if they want to.

That's why everyone was clamoring to become beggars.

However, begging was a miserable profession.

Since beggars don't produce anything of value, the things they could enjoy were inevitably limited to each city.

So, in the end, beggars were a group of people who had something that another beggar could not have.

Even the few coins that were occasionally thrown out of kindness were not distributed evenly or fairly among all the beggars.

So, even though they all lived by begging, they competed with each other and were ridiculously jealous of each other.

Just look at where they beg. It's no exaggeration to say that the best spots, such as those on busy streets, were literally created by the blood of beggars.

For a few pennies, or a better begging spot, they would fight with knives, or if they didn't have knives, they would fight with stones or clubs, killing each other.

In any case, the beggars that Qing had encountered were such despicable trash.

Just look at the guy with the club over there.

On the surface, he looked like a beggar, but with his strong arms and legs and clear white eyes, he must be a strong young man.

In Zhongyuan, if you have healthy arms and legs, you could find work anywhere.

There was always a shortage of farmhands, and even if not, there was always odd jobs to be done, such as building houses or carrying loads, in Zhongyuan.

Then why were they begging?

Strong beggars lived a comfortable life by exploiting weaker beggars.

Even now, it was probably part of their rule to exploit others.

A young beggar who has been severely beaten scrambled to pick up the food that has spilled out of his torn bag.

Qing was frustrated of this sight.

\textit{Oh no, food or not, you have to run away first. Who has time to pick that up now?}

Sure enough, beggars have quietly taken up positions on the other side of the road.

His escape route has been blocked.

Meanwhile, a beggar with a club, who appears to be the captain of the beggars in that area, tapped his palm with his club to make a sound.

Qing quietly get up from her seat.

The stick the beggar held in his hand was not just a stick.

Because—

In fact, begging was a pretty decent job if you give up a few minor conveniences.

So, you gave up cleanliness and lived in filth, gave up delicious food and eat garbage, gave up a good place to sleep and slept in an uncomfortable, smelly, dirty place infested with bugs, and gave up resisting the cold, heat, rain, and snow—just accept nature as it is, whether it snows, rains, was cold, or hot—

And if you get sick or injured, you can just gave up on treatment and die instead.

Yes, just die.

There were almost no physicians in Zhongyuan who treated beggars for free.

The reason that it was 'almost' was because if you looked hard enough, you might find someone like Langzhong Daren.

Even so, medicine in Zhongyuan was so poor that even minor wounds can be fatal. (This was a limitation of the times, and the same was true anywhere in the world.)

So, after being beaten with clubs, the beggar would suffer and die.

And don't other beggars know this?

It's just that they didn't kill them with their own hands, but beggars knew better than anyone else what happened to beggars who were beaten to death.

The reason they didn't kill them with their own hands was also very selfish.

The government only looked away fom martial artists, but they were a very terrifying group to the weak.

So even if they were beggars, if they kill another beggar in broad daylight, the government would step in and punish them, so they don't kill them directly, but left them to die by their own.

What happened when the beggar who was beaten to death dies?

The other beggars would carry the body around, crying and begging for pity, and when winter comes, the season when beggars would starve, well, you know…

"You filthy plague-ridden bastard, I left you alone because I didn't want your disease to spread, but now you're stealing people's food? Should we just leave this plague-ridden rat alone?"

"Who, who's the plague-ridden bastard? I'm not the plague-ridden bastard!"

The young beggar screamed.

\textit{Oh, he's got some spirit.}

Of course, it didn't do any good.

"What's that? Where's that rat squeaking?"

The captain beggar scratched his ear and asked, and the other beggars burst into a wicked laugh.

"Hey, catch him! We'll break his legs today. Hehe, that plague-ridden brat deserves to be made to crawl like a bug."

"Stop, let me go!"

The young beggar struggled while being held down.

Qing sighed deeply.

Cruelty sometimes becomes authority.

It seemed that his intention was to beat one of them to death and show off his ferocity.

Even in this situation, people just stood by and watch, since if the beggars killed each other, it would reduce the number of beggars.

And if you mess with people who have nothing, you won't get anything good out of it.

"Stop."

Her voice was imposing, but rather than intimidating, it was beautiful and melodious.

The beggars hesitated.

In Jianghu, one was told to be careful of children, women etc., but that advice applied only to martial artists.

For those who were not martial artists, whether they were children or women, if they were carrying a decent sword, you naturally had no choice but to be on high alert.

Moreover, her sword was quite large.

"If you're a beggar, hide in a shady corner and beg, don't dare to show your face in broad daylight."

The captain of the beggars froze.

If she had provoked them with her usual vulgar insults, they might have been less afraid.

These days, it was fashionable for female martial artists to cover their faces, so it was not unusual to see a female martial artist wearing a veil.

However, it was difficult to guess the age of a woman from her voice.

Even with her face covered, she sounded like a seasoned martial artist with a solemn tone.

"No, Master, that's not it. It's a misunderstanding."

"A misunderstanding? What misunderstanding is there?"

"No, no, that guy was a Bai, a member of the Bai tribe. There's been an epidemic of smallpox called Bai Pox in this area lately, so… That's why we're doing this. It's a good job, cleaning up the rats that spread the disease…"

A deep wrinkle appeared on Qing's forehead.

Somehow, even though the kid was dirty, he looked fine with no scars on his faces, so it didn't seem right to call himm plague carriers.

\textit{That Bai Pox nonsense again.}

\textit{It's an attempt to make the entire Bai tribe the enemy and drive them out. Now it's clear that the Blood Cult's schemes are not ordinary.}

Qing snorted in derision.

"You don't understand what I'm saying. You said that even with your limbs intact, you're a filthy beggar who dares to show your face in broad daylight, didn't you?"

"What?"

"I don't care what you lowly creatures do. But you came out and showed me your filthy faces, forcing me to smell your rotten stench. I am asking you to answer for the crime of offending me."

She simply said that their very existence offended her.

It was a completely unreasonable argument, asking why they were ruining people's moods by standing out.

So, does that mean beggars have to hide away so they don't catch people's eyes?

However, the female swordsman's voice was so sincere that anyone could hear the anger in her words.

Anyone could tell it's a chilling growl of someone who had a grudge against beggars.

The beggars captain's expression hardened.

They had been caught red-handed.

Martial artists should be careful not to look down on female martial artists, but to the common people, female martial artists were even more dangerous than male martial artists.

Since they were always ignored, they tended to be more vicious and would get angry over the smallest things, claiming that they were being ignored.

What should the captain of the beggars do?

Should he stood up to her?

Unfortunately for Qing, the captain of the beggars immediately knelt down and bowed his head.

"Oh, Master, I am sorry! I did not know that you are someone so important. If I had known, I would not have done that. I am truly sorry. I have committed a capital offense! Please have mercy on me…"

"It's not a capital offense."

"Then, may I leave now…"

"That doesn't mean you're not guilty. Let's see, you offended me, so I'll let you go if you each give me one of your arms."

Cutting off an arm usually killed a person.

It might be different in Qing's homeland, but in Zhongyuan, it was not easy to survive with an arm cut off

Furthermore, a rat in a corner will bite a person.

In the end, the captain revealed his true colors.

"Damn it, what the hell is this? Boys, beat her up!"

Then the beggars rushed forward in unison.

However, they did not rush toward Qing.

They began to rush toward an unknown enemy on the opposite side.

Of course, the first to turn his back was the captain of the beggars.

It was a typical trick of beggars to try to escape while their gang was buying time.

His subordinates must have known what their captain was like, so they also ran away without hesitation.

\textit{Hmm, they scattered in all directions, running away in panic, like insects fleeing when a rock is lifted.}

\textit{They really look like vermin.}

\textit{That's what beggars are like.}

Of course, Qing had no intention of letting them go.

At least the captain must be dealt with.

If she let them go, they will hide for a while, but eventually, with their healthy bodies, they would gather another group of beggars and continue their mischief.

Qing stomped on the ground.

What can a beggar who knew nothing about martial arts do?

In an instant, Qing's new technique stretched out.

Followed by a flash of her sword, there was a satisfying sound, and she couldn't help but smile.

"Aaaaah!"

The scream was truly loud, and this was the pleasure of hearing it with her ears.

\textit{That's right, bad guys should run away and beg for mercy, crying and sniveling, even if it means living a sinful and useless life.}

\textit{That way, the person who cuts them down will feel rewarded.}

\textit{In that sense, those Five Poisons Sect guys are… ugh.}

Qing pointed the tip of her sword at the Captain Beggar's nose, who was crying out in pain.

Then, as if he had come to his senses, the Captain Beggar forgot the pain of his severed arm and looked up at Qing with trembling eyes.

He looked up at Qing with trembling eyes, hiccuping in surprise.

"Get lost. Don't forget to take your dirty arm with you. Roast or bury it. Otherwise…"

A vivid red sword Qi glistened on the blade.

"Yes, yes!"

The captain of the beggars hurriedly picked up his arm, but then stumbled and fell heavily. However, he got up quickly as if he felt no pain and ran away.

Seeing this, Qing's face broke into a broad smile.

\textit{Phew, I got rid of a big piece of trash today.}

\textit{Anyway, we have to exterminate all these beggars.}

Qing turned around.

With everyone running away, the young beggar who had been freed was staring blankly at Qing.

Then, thinking that Qing was looking at him, he was startled and jumped up and ran away.

At that moment, Qing was not a chivalrous warrior who saved a boy in danger, but a foul-mouthed female swordsman who hated beggars.

He had been making poor decisions since earlier.

He fell down and picked up food instead of running away.

In a situation where he was not sure if he would survive even if he beghed for his life, he argued that he was not a plague victim.

Now he just stood there watching until the terrifying female swordsman turned around to look at him.

How can he survived the harsh life of a beggar like this?

Even if you're quicker than others, it was hard to survive in this hellish world where everyone fought and devoured each other.

Wasn't the first thing young beggars learn how to survive and be servile?

He was not like other beggars.

\textit{Does that mean he hasn't been a beggar for long?}

\textit{But that makes me even more interested in him.}

And he's a plague victim?

Once you're labeled a plague victim, you can't live a normal life, even if you want to.

These involuntary beggars were not the kind of beggars she was talking about.

Even if a strong-bodied beggar ran away, Qing will catch up with them in no time.

No matter how fast a young beggar runs, there was no way he can escape from her grasp.

Qing grabbed the young beggar by the back of his neck and lifted him up high.

The young beggar dangled from Qing's hand, flailing his arms.

"Uwaah! I'm sorry! I won't do it again! Please, let me go!"

It seemed that he could defy the captain of the beggars, but not a martial artist.

Qing spoke in a gentle voice, as if to reassure him.

"Hey, are you hungry? Don't eat leftovers or scraps from other people's meals. If you eat anything, you'll be in big trouble."
