\chapter{If You Want to Kill Someone, Prepare Two Graves (5)}

The merchant Jong Yeol-jung had married a Bai tribe woman named Cheon and had two sons with her.

Unfortunately, the Bai woman, Cheon, grew weak after giving birth to the second child and eventually passed away.

However, that did not leave the position of the mistress vacant.

As was common with successful merchants, Jong Yeol-jung already had a beautiful second wife.

"That woman, Lady Lee, was originally my dad's—no, my father's second wife."

"Somehow, just hearing that much, I can already guess the rest. Your father passed away, and that woman drove you out, right?"

This was an all-too-common story in Zhongyuan.

The notoriety of second wives was practically universal.

The schemes they employed to ensure their own sons inherited the family were numerous and vile.

In fact, the harm they caused was so severe that it was outlawed by the state.

Any second wife or concubine who harmed the legal wife or her children was punishable by death without exception.

Of course, the second wives might have their own grievances.

Typically, the legal wife harbored deep resentment and hatred toward the second wife and concubines who monopolized the husband's affection.

Thus, when the husband died, it was all too common for the vindictive legal wife to drive out the concubines and their children.

In some cases, this was even legal!

So, for second wives and concubines, scheming was a necessity to secure their survival after the husband's death.

This was so common in Zhongyuan that historical records were filled with accounts of such 'concubine rebellions'.

If one were to label the societal ill of allowing multiple wives, it might be called the "Rebellion of the Second Wife."

However, even within these rebellions, there were degrees of severity and cruelty.

About a month ago, the merchant Jong Yeol-jung was found dead overnight.

The physician declared it was due to Bai smallpox, and the enraged magistrate held the two sons responsible for their father's death and drove them out.

They were branded as the villains who spread Bai smallpox and the unfilial sons who killed their own father.

"Dad was a healthy man. He practiced Tai Chi every morning and evening and was sturdier than most laborers. How could he suddenly die overnight? It's obvious—that woman and the general manager poisoned him."

The inconsistency between 'dad' and 'father' aside.

That wasn't the important part.

"Do you have proof? And the general manager, you say?"

"There were suspicions that woman and the general manager had been intimate for a long time. Someone even claimed to have seen them leaving the same room, but it was dismissed as a misunderstanding, or perhaps people just pretended not to know. I should have told Father—no, Dad—back then."

"Brother…"

"And a few days before that, I saw it myself. Those two, arm in arm, walking intimately at night, whispering…"

Qing knew well how people tended to twist stories in their favor.

Thus, Jong Mun-woon's claims were merely personal opinions without concrete evidence.

Even if the family head and the general manager were close, that wasn't unusual.

Since their birth mother had passed away long ago, the second wife would have naturally taken over as the legal wife, managing the household affairs.

So, discussing household matters and finances with the general manager wasn't inherently suspicious.

But the bigger picture was undeniably strange.

First, based on Qing's observations in the quarantine zone, this disease wasn't deadly enough to kill a healthy person overnight.

In fact, diseases that could kill a healthy person instantly were exceedingly rare.

And yet, the man died suddenly from the supposedly nonexistent Bai smallpox?

The general manager, in a fit of rage, declared the sons the source of the disease and drove them out, calling them the most unfilial sons in the world?

Normally, if a stepchild died, wouldn't one vow to take care of the remaining children?

And what about the scene Jong Mun-woon claimed to have witnessed?

Lady Lee, having driven out the sons after the merchant's death, became the widow and new head of the household.

Yet, she was seen walking arm in arm with the general manager at night?

Anyone in the world would see this as clear evidence of their conspiracy.

Only the lack of physical proof remained.

"Damn it, those bastards."

Qing stood up abruptly, furious.

"Let's go. I need to see those two with my own eyes."

"Benefactor, I'm grateful, but… the general manager has powerful connections. The authorities will surely side with him. I don't want you to face trouble because of us."

Jong Mun-woon's expression darkened with worry.

Qing ruffled his hair affectionately.

Such consideration from someone so young was touching.

"Ah, worrying about me too?"

"Benefactor? Um, the head-patting was a bit…"

Jong Mun-woon's face turned bright red.

The cool fingers were incredibly soft, and the faint scent from the fluttering sleeves was intoxicating…

"And connections? What's that? I have connections too. Let's go. I'm not helping you out of charity, I just won't be able to sleep if I don't see the end of this. This is entirely for my own sake."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A servant rushed onto the terrace in a panic.

"Sir—no, Master of the Trading Company! Have you heard the news?!"

"Haha, you fool, shouting like it's the end of the world. Who's the 'Master of the Trading Company'? If others hear, they'll misunderstand. Call me the elder brother who took over after the younger brother's passing."

"But, sir! Our late master worked so hard to build this trading company, and you've been managing it so splendidly!"

The man called 'Master of the Trading Company' didn't seem displeased. In fact, he smiled warmly.

He didn't seem to care about others' misunderstandings.

Especially since the woman clinging to him was the widow of his late brother.

To outsiders, it was an unsavory sight.

But the two looked blissfully happy together.

That is, until—

"Are… were the young masters here?"

Lady Lee's expression darkened instantly.

"What young masters? The only young master is the one in my womb. Are you suggesting there were others in this household?"

"Ah, my dear, you're right. For the sake of the child in your womb, you should only see good things, hear good things, and keep good people around. Like me."

"Oh, you…"

They laughed together, utterly pleased.

Then, the man asked casually,

"So, Servant Yu, what's the matter? Did those unfilial sons who killed their father die? Ah, what a shame. I was planning to discipline them properly and bring them back after their three-year mourning period, but they couldn't even last a month. Tsk. How weak must their upbringing have been?"

There was no trace of pity in his tone.

Beside him, Lady Lee also bloomed into a radiant smile.

"Actually, no. A martial artist appeared and took the young masters—no, the children—away…"

"What? A martial artist?"

The couple's expressions darkened instantly.

Martial artists were a troublesome bunch.

They didn't just ignore the law, they didn't even pretend to follow it.

They called themselves 'chivalrous heroes', but in reality, they were no better than bandits.

They lazed around, occupied territories, and extorted protection money under the threat of their blades.

What kind of righteousness or chivalry was that?

But beyond the merchant's deep-seated hatred for martial artists, this news was alarming.

"Is it someone famous? How skilled are they?"

"It is a woman. I don't know her reputation, but her sword gleamed terrifyingly, and she could leap ten paces in a single bound…"

"Damn it!"

The man shot to his feet.

Of all times!

He had just sent away the wandering martial artists he usually kept around for protection and was in the process of hiring new ones.

And now this happened.

"My dear, if it's a martial artist…"

"Chaos is coming. They'll definitely interfere. First, we'll ask the local elders for help and hire men from the Five Poison Sect. *Ahem.* My dear, we'll have to spend generously."

"Spend? How much?"

"Enough to ensure they take care of it…"

Lady Lee's eyes sharpened.

"I told you we should have hired assassins from the start. You skimped on money and kept those useless beggar brats around. And those brats couldn't even kill a few weaklings!"

It was an outrageous thing to say.

But the man brushed it off.

He already knew her nature.

"Ah, if I'd known it would come to this… I heard there's a famous master in the western district. I was planning to use that money to hire him as our child's martial arts teacher, a great master."

At the mention of 'our child', Lady Lee's expression softened slightly.

Had Qing heard this, she would have been furious, every word out of their mouths was a capital offense.

"Ahem. The issue now is the money. First, we must stop that martial artist. Thankfully, I've shown proper respect to the local elders and the Five Poison Sect. They'll surely send plenty of men."

He then called for his aides.

"Chuil! Chui! Chuil, go to the authorities and request help. Tell them a martial artist is causing trouble, they'll understand if you say it's getting out of hand. Promise proper compensation later. Hurry. Chui, go to the Five Poison Sect and deliver the same message. Offer a year's worth of protection money upfront."

His response was swift.

But Lady Lee was still uneasy.

"My dear, what if it's a terrifyingly strong master?"

"Pfft. A truly powerful master wouldn't come to this backwater. Unless it's someone from the Diancang Sect—hey, Servant Yu! Servant Yu!"

"You called, Master—no, General Manager."

"Is the master from the Diancang Sect? Right?"

"Unlikely. Anyone would recognize a Diancang Sect disciple's uniform. Since no one mentioned it, it's probably not them."

"Whew. Then we're fine."

The man sighed in relief.

"My dear, then it's okay? I can relax?"

"If it's not a Diancang Sect master, it's nothing. My dear, martial artists are like those street thugs, they don't dare cause trouble in others' territories. Once the Five Poison Sect and the authorities arrive, they'll back off. They're no different from bandits, they flee at the sight of officials."

"Then it's fine? I can trust you?"

The man thumped his chest confidently.

"Trust me. Oh, my dear, you've had such a scare. Let me hold you."

"Oh, you…"

The two embraced, utterly pleased.

Even though this was hardly the time for it.