\chapter{If You Want to Kill Someone, Prepare Two Graves (4)}

First of all, these brothers didn't even look human.

Anyone can see they're just beggar brats.

Beggars weren't people.

Just look at the waiter's reaction.

"Ah, sir. Our inn prides itself on being high-class. Letting beggars in is a bit… And, though your heart is kind, these brats are of the Bai tribe—disease carriers. How could you suggest letting them into the inn? Who would want to stay at such a place?"

The waiter whined with a pitiful expression.

At this, the older beggar looked resentful, while the younger one shrunk back with a tearful face.

Qing was about to say something but hesitated.

Qing knew the Bai tribe's smallpox was just a trick of the Blood Cult, but these commoners genuinely believed it. Even if Qing called it nonsense, they wouldn't listen.

Besides, with the Blood Cult swarming the nearby Five Poison Sect's headquarters, it wasn't the right time to argue.

And, while the premise was wrong, the waiter's point wasn't entirely without merit.

Who would want to stay at an inn housing sick people?

\textit{Well, what could be done?}

\textit{As the saying goes, the thirsty dig their own wells. Surely there's an inn somewhere in the neighborhood willing to take in Bai beggars.}

"Is that so? Then I'll find another inn. I paid for ten days in advance, right? I'll vacate the room, minus the last two days—"

"Now that I think about it, there were no other sick people in the city. Not all Bai tribesmen carry diseases. If they were contagious, it would've spread by now."

Of course, the waiter's tone changed the moment Qing mentioned leaving.

Business wasn't going well, after all.

Losing a guest who booked the best room and spent money lavishly was unthinkable.

Though that money was left behind by the Five Poison Sect members, payment for sending them to the afterlife and fulfilling their dying wish for revenge.

Truly, even villains leave money behind when they die.

"Prepare a bath for me. First, food—we need to eat. Waiter, what's good today?"

"Hehe, today we have…"

And so, the inn entry was a success.

Qing never liked private rooms.

Eating in a closed-off space felt stifling. Qing preferred to watch the surroundings and eavesdrop on conversations while dining.

If luck was good, some villain might even cause a scene, offering a chance to enjoy some action.

Wearing a veil while eating had long become second nature, so it wasn't uncomfortable.

Of course, when with companions, especially that troublemaker Goon-yeong, whose table manners were atrocious, Qing would book a private room to avoid embarrassment.

But this time, the inn insisted, and there was no choice.

Having beggars suspected of carrying diseases sit in plain sight, especially in the prime seating area (where expensive dishes were displayed prominently), was unthinkable.

So Qing entered the private room and removed the veil.

"Wow…"

The younger beggar gasped in admiration.

Qing's face alone was worth a million gasps, a beauty so radiant it didn't need lighting, the finest in the world.

The boy was also staring blankly.

Qing giggled and flicked a finger.

"Hey, don't wear out my face staring. So, what are your names? I can't just call you 'big beggar' and 'small beggar.' Unless it's 'small beggar' and 'even smaller beggar,' but that's too long, right?"

The boy stood up and clasped his hands in greeting.

He must have seen it somewhere.

"My apologies for the late introduction. I am Jong Mun-woon."

"I'm Jong Mun-gan…"

"Um, Benefactor, may I ask your name?"

"Hmm, I'm in a bit of a situation where I can't share my name. Just call me 'Benefactor.' So, how did you end up as beggars? You don't look like you were born beggars."

No one was born a beggar, after all.

But the lack of the typical beggar's submissive resignation made it clear they weren't always like this.

"Well…"

At that moment—

"Sir, we'll serve the prepared dishes first."

Zhongyuan cuisine was known for its strong heat and oil, ensuring quick service.

Higher-end dishes take more time, but most were prepped in advance, so delays were rare.

Qing put the veil back on.

No need for rumors of a beauty to attract gawkers, people pretending to stroll by, crowding the place.

Soon, plates of food began clattering onto the table.

Then, the older beggar looked at Qing.

A strange glint in his eyes, slightly resentful?

"What? Why?"

"N-no, nothing."

Jong Mun-woon glanced at the lavish spread before Qing, then down at the single bowl of plain rice porridge in front of him.

A watery gruel with no ingredients, just rice and water.

Honestly, it was a pitiful sight.

Qing had a table full of expensive dishes, while the beggars got a single bowl of bland porridge?

Even charity shouldn't be this insulting.

Qing burst into laughter.

"If you eat something you're not used to, you'll get sick. After surviving on scraps for so long, suddenly eating rich food could kill you. A stomachache is one thing, but a ruptured gut? Deadly."

"Ah…"

Sadly, Jong Mun-gan's condition was poor, and while Jong Mun-woon was sturdier, he wasn't much better.

"For the next two days, you'll eat porridge to recover. Today, it's plain rice porridge. Tomorrow, something tastier. The day after, something with litlle oils."

Relief washed over Jong Mun-woon's face.

\textit{Had he thought they wouldn't get any food?}

\textit{Of course, food is important, but what did he take me for?}

Though his relief was less about the food and more about the mention of 'tomorrow' and 'the day after'.

From the refusal to share a name, he'd feared they'd be kicked out after one meal. 

Hearing otherwise brought relief. Naturally.

And so, the meal began.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Brother, it's hot…"

"Bear with it."

"Hng, it's hot…"

The scalding bathwater was uncomfortable for the younger one.

That was natural for a child.

But it didn't last.

The sensation of hot water searing the skin, the heat like ants crawling through the veins, biting away fatigue, the warmth of the bath.

Given time, the fatigue would melt away, leaving the body limp and the mind pleasantly drowsy.

"Hehe, brother, the porridge was delicious…"

"Yeah."

"I want more…"

The boy thought of the rice porridge.

No foul smell, no sourness, just clean, hot rice porridge.

The more he chewed, the sweeter and nuttier it became.

Had porridge always been this delicious?

The best bowl of porridge in the world.

And those hands—

"Hmm, is plain porridge too boring? Here, this should be fine. Don't blame me if your stomach hurts later."

The slender, pale fingers that squeezed the chicken breast dry, shredded it thinly, and placed it on the porridge.

Jong Mun-woon swallowed hard.

Sure, it was dry, flavorless chicken, the driest of the dry.

But to the boy, it was ambrosia.

The moment he chewed, his world brightened.

How delicious that chicken was…

He thought of the benefactor again.

So chivalrous heroes really existed.

And such a beautiful woman—unlike any he'd ever seen.

The kind of hero from stories, no, even beyond stories.

In tales, beautiful women were usually the ones saved by heroes, not the heroes themselves.

At first, he'd thought she was older, maybe his mother's age, but she couldn't be past twenty. It was shocking.

Then—

Creak. The door opened.

Clack! The sound of stones hitting each other.

Turning, he saw the benefactor through the steam, her face veiled.

Her sleeves rolled up, revealing slender, translucent arms. She clacked two stones together.

"Well, scrubbed clean yet? Time to exfoliate. The dead skin's gotta go. You'll shed a whole layer today."

"W-what are you doing!?"

The boy yelped in shock.

But the benefactor's voice was calm.

"What? Exfoliating. When else would you do it? Do it properly or not at all. Half-hearted scrubbing is pointless."

"B-but, a man bathing, even if you're our benefactor, we can handle it ourselves—"

"Man? I've no interest in watching grown men flail. But you're not men. You're kids. Minors. And weak ones at that."

"Minors? Benefactor, I'm—"

"Eh, no need for shame. Adults look after kids, that's normal. Count yourself lucky. I'm helping because you're kids. Grown-ups fend for themselves."

"Huh? B-but, I'm fine! I'll do it myself!"

"What's this? Maturity? Grew up fast? Exfoliating's hard work. You should be lying down and saying 'thank you.'"

"Really, I'm fine! Please, just—"

"What, you think I'm forcing you? I'm not wasting energy on stubborn kids. Here, clean clothes. Scrub well, polish up, then get dressed."

With that, she left as abruptly as she came.

"Brother, you turned fifteen last year…"

Fifteen, the age Confucius declared he devoted himself to study.

Turning fifteen last year meant he was sixteen now.

By Zhongyuan law, sixteen was adulthood for men, old enough to start a family.

"Shh."

"But…"

"Later. We'll explain later."

Didn't the benefactor say it herself?

She helped because they were kids. Adults fend for themselves.

If it were just him, maybe. But for his brother's sake, until he recovered, they had to rely on her.

His small, frail frame, always a source of insecurity, had unexpectedly become useful.

Of course, Jong Mun-woon was mistaken.

Qing's standard for adulthood was nineteen.

Sixteen was still a child, a baby, really.

Back home, even new recruits fresh from military service were called 'kids'.

But that was Qing's hometown standard. In Zhongyuan, only Qing held this view, so the boy had no way of knowing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Oh, you've got noble features! I knew you weren't born beggars."

Indeed, the washed-up Jong brothers, though gaunt, still carried an air of nobility.

'Noble features' just meant they were handsome.

Talented men often married beauties, and their children inherited those looks.

Wealthy families intermarried, refining their lineage over generations, resulting in exceptional looks.

"So, how'd you end up beggars?"

The question wasn't deep, just small talk.

"Well, our dad—ah! Ahem, um, our father was a great merchant…"

Huh?

At barely over ten, 'dad' rolled off the tongue easier than 'father'.

But why did he struggle so much to say it?

His face turned red, as if forcing the word out.

But the thought was fleeting.

Listening to their tale of overnight beggarhood—

"What! Those bastards!"

Qing erupted in anger.
