\chapter{If You Want to Kill Someone, Prepare Two Graves (11)}

The tremors in Jong Mun-woon's body subsided.

Could there really be such a reliable person in the world?

It felt as if he would always be on my side.

Jong Mun-woon began to speak.

It was a more composed question than he himself expected.

"Uncle, you have treated me well. You played with me a lot. Was all that a lie? Were you afraid of angering my father?"

"No. I simply wished that you would not become like your father. Your father thought the same, believing that if you grew up loved, you wouldn't go mad. Your grandfather, however, was a cruel man even to his children."

"Was it sincere? Truly?"

"If it had not turned out this way, if your father had not gone mad until your sister was born, you would have cherished a sibling who didn't resemble you. Then, I would have remained your good uncle forever."

"Then why, why did you kick us out…"

"Once he became a father, I could not allow even the slightest possibility. A clever lad like you would question the unnatural death, and I feared the truth would be revealed later. It was only a matter of prioritizing my own child over a nephew, but I am sorry for having done such a terrible thing to you."

The chief administrator continued calmly.

"Yes. I am indeed as dreadful a sinner as your grandfather and father. They prepared people to kill, and I took care of the aftermath. So, bear with me. I was to be treated as the worst of mankind, having my limbs cut off and displayed in public."

"…"

"However, your stepmother was different. She was a pitiful woman. Pity her. She was deceived into marrying because she caught your father's eye, but since then, she hasn't had a single moment free from bruises on her body. Even though she is with this scoundrel, had it not been for that, she would have taken her own life long ago, a sad woman."

"Gege! No, that, Young Master, it's my fault. Just once, just once, please forgive him. Okay? I did wrong…"

Lee was holding onto the hem of his pants, weeping as she sought forgiveness.

Jong Mun-woon clenched his fists tightly.

"I…"

Jong Mun-woon squeezed his eyes shut.

His mind was filled with the stories he didn't want to believe.

The caring father was actually a murderer who had gone mad.

The uncle he had trusted tried to kill him and his sibling, colluding with his stepmother.

Yet, his uncle and stepmother too, must have suffered greatly because of his father…

But what wrongs had he committed?

Setting himself aside, what about Moonyeok, his little brother, what possible wrongdoing had that innocent child committed? Were it not for the benefactor who helped, his brother might not even be alive right now.

At that moment.

A cold hand firmly held his shoulder.

Suddenly, a cheerful smile flashed brightly in Jong Mun-woon's mind, one that belonged to a beautiful person.

Yes. The benefactor was still around.

He didn't want to forgive them.

But since he had nearly died yet hadn't, they didn't need to die either.

He wouldn't press charges for killing his father.

No, he didn't want to.

It wasn't because of the shame of his father's identity as a murderer; rather, if he were to seek vengeance, he too would have to inherit that blood price.

For the sake of being right in front of the benefactor, he must ensure that both he and his brother remained innocent.

For the sake of being upright before the benefactor.

"You both should just leave."

The strength drained from Jong Mun-woon's shoulders.

His expression had also relaxed, as if he had laid down a heavy burden, turning to bow his head toward Ji-hyun.

"Magistrate, originally it is only right for a child to atone for their father's sins. However, I dare not inherit the legacy, thereby wishing to avoid such sins. Thus, Jong's son cannot be held responsible for his father's death, and therefore there's no qualification to request retribution against those heinous ones."

Since he wouldn't be inheriting any assets, implying that he would pass the estate onto the coffin, he requested that it be regarded as a severance.

The expression on magistrate's face brightened somewhat.

Having not brightened too openly was due, after all, to the presence of the Inspector.

Qing seemed a bit surprised.

Jong Mun-woon, who appeared to be just a little over ten years old from the outside, seemed to be about that age, or so Qing thought.

\textit{What is going on? How could he speak so well?}

\textit{I knew he is precocious, but is he a genius?}

\textit{How unfair it is that my daughter, apart from eating, sleeping, and doing her business, isn't particularly skilled at anything in this world.}

\textit{Of course, Ciyu is certainly much cuter.}

\textit{But really, if cute is all it took, that is just fine. Healthy is good, hmm, somehow it felt like tears are about to come.}

"Furthermore, those who wished to harm both me and my brother ultimately could not fulfill that desire, and now that we were merely unrelated bystanders, I feel sorry for their lamentable plight, thus I will forgive them."

In reality, this was a somewhat deflating conclusion for Qing.

They said the best revenge was forgiveness.

This might sound ridiculous, but it was just noise when others were in other people's affairs.

But when the person forgiving said it, after all, it wasn't entirely wrong.

Revenge was carried out to live, to calm that burning sense of grievance and to soothe one's own upset heart that nearly bursts from injustice.

But if through forgiveness, one could find peace of mind, then for that person it could be the very best revenge.

"Ahem, if this was truly your intention…"

The magistrate shot a sidelong glance at Qing.

When Qing nodded, the magistrate's expression became very solemn.

"With this, I shall conclude the judgment! The children of the Jong family shall not be subjected to any disadvantage because of their father's conduct! Furthermore, the total responsibility of the estate and the Lady Lee's crimes were hereby absolved, but they must promptly leave the village!"

Wow!!

As if they had just seen a great spectacle, the villagers cheered and felt compelled to join in the ruckus.

"Young Master, thank you, thank you. Thank you! Hic, thank you…"

Among them, Lee sobbed out her gratitude while the chief administrator just bowed deeply, showing the top of his head.

Some villagers couldn't hide their tears of joy.

Qing felt somewhat awkward about it.

\textit{Hmm, is this really something to be moved by?}

The chief administrator and Lee held tightly onto each other as they left.

Although they were being expelled empty-handed, the looks exchanged between them were affectionate, and their steps forward were unwavering and strong.

Thus, the incident regarding the Jong family came to a close.

……But for someone, it was not the end.

"Cough, I will kill, I will kill him."

It was a man in a pitiful state.

Barely able to shield himself from the rain, his hair was matted and dripping with grease, making it quite disheveled.

His clothing was in tatters, a filthy sight covered in dirt, and his exposed skin was just as filthy.

However, that wasn't particularly surprising.

Anyone who saw the man would have said this.

Ew, what a beggar.

Yet, this beggar was dramatically different from the rest.

He was missing one arm!

However, in Zhongyuan, beggars tended to be survivors rather than mere victims.

Losing an arm didn't particularly help in begging, which was somewhat unfortunate.

"I'll kill him…"

Moreover, he was constantly crying out for revenge.

At this point, even inebriated old men glaring wasn't enough to scare someone trying to beg.

But the beggar was indifferent to begging.

He was only burning with boundless hatred.

Hatred for those who had reduced him to this state, to the pathetic one-armed form he now bore.

Hatred for those bastards of the Jong family who caused him such ruin.

How could he not?

Although he was ordered to kill that child, it was not at all his doing, and yet he found himself in this horrific situation!

In Zhongyuan, without antibiotics, losing an arm meant that even with a good physician nearby, life was hanging by a thread.

Having tied himself to stop the bleeding barely, the infected wound was decaying, yellow pus oozing out, and fever raged through his body, completely preventing any sleep.

In that dreamlike haze, it was impossible to distinguish whether it was a dream or reality, only pain and more pain, excruciating agony.

When the time came when he was the leader of the beggars in Jinping County, those beneath him would laugh and kick him once he fell.

But, that hatred pushed the beggar onward.

He wouldn't be the only one suffering this terrible fate, so he would see to the end of those bastards who had ordered him to kill the boy, who were directly responsible for this fate.

And now, at this very moment, among the cheering and emotional commoners.

In the beggar's eyes, amidst the unforgiving fury, madness surged with a dangerous hue.

Now, surely those horrific enemies would cling to each other's hands, refusing to separate.

This couldn't be happening. No, it wouldn't do.

Among the crowd, a beggar slipped away unnoticed.

No, rather, they might have felt relieved that the crazy beggar who could scream about killing had backed down.

Thus, armed with a rusty but sharp blade hidden within his rags,

With intense murderous intent, he vanished, pursuing the pairs of the expelled man and woman.
