\chapter{If You Want to Kill Someone, Prepare Two Graves (1)}

Deep in the northern ridge of Dazhai Mountain, a scene that was impossible to look at unfolded, a scene that could only be described as hell on earth.

Collapsed military tents stood desolately, and between them were human corpses, or what used to be human corpses.

With almost no intact bodies remaining, it was difficult to even call the scattered fragments of flesh and bone "bodies."

Moreover, at the center of it all, corpses were piled up like mountains, a sight that seemed to epitomize the fate of a defeated army slaughtered to the last man.

Of course, the bodies piled up like mountains were not stacked there by someone for disposal, but were merely the result of the dying Odokumons rushing in and stabbing them with their swords.

And from that mountain of corpses, someone's hand suddenly twitched.

There were survivors!

Among the Five Poisons Sect, who had shouted 'Death to the enemy' and sacrificed their lives in a special attack, were there any survivors?

"Ugh, it doesn't look like they're dead at all."

It was unfortunate for the Five Poisons Sect, but the survivor was the Heavenly Blossom Sword.

The reason why Qing had been lying on the pile of corpses was simple.

If any of Five Poisons Sect's followers remained, wouldn't they appear to collect the bodies of their own people?

When you do something, you have to do it thoroughly. Now that it has come to this, if she didn't eradicate them completely, won't the grudge they speak of, the chain of revenge, unfold again someday?

Yes, that's right.

The only way to break the cycle of revenge was not through forgiveness, but through total annihilation, by killing all those who would seek revenge.

Of course, it wasn't just that thought alone that kept her from spending the night under the pile of corpses.

There was another reason.

It's too tiring…

\textit{Since becoming a true master (Hwa-kyung), had I ever been this tired?}

\textit{I was chased and pursued by the Five Poisons Sect, rampaging and experiencing every kind of unpleasantness imaginable.}

\textit{Thanks to that, I exploded, and when I fought the Daiyue soldiers, I was almost out of control, copiously using my Demonic Arts.}

After that, in the final battle with Five Poisons Sect, it wasn't a thousand changes\footnote{Countless Changes is written using 'thousand' character}, but a hundred changes, or rather, not quite a hundred, but roughly fifty-five hundred changes, which drained her inner arts.

She was surrounded by vicious creatures that rushed at her, biting and clinging to her like a pack of dogs.

Her Inner Qi and physical strength were completely depleted for the first time in a long time, so she was completely drained, as they say in Qing's homeland.

So, she decided to get some sleep first!

If she left this place carelessly, there might be someone who survived, and in the distant future, the Five Poisons Sect might be revived, or remnants might come to collect the bodies, or Daiyue's soldiers or the Blood Cult might show up.

If she closed her eyes during this time, it will look natural, and it will be easier to launch a surprise attack than to sneak out carelessly.

Is there any reason not to do this?

The body was covered in blood, and the flesh was soaked in it, which was unsettling.

But the expression used in such a situation was 'an abandoned corpse'.

Every inch of my body was covered in mud, sticky with sweat, and reeking of a pungent poison, leaving her in an indescribably filthy and disgusting state.

What difference would a little more corpse water make?

Anyway, she lost consciousness last night, and when she opened her eyes, the morning sun was already up.

Even when tired, a master was a master. No matter how tired she is, if she sensed someone approaching, she would have opened her eyes immediately.

Seeing that time had been passing like this, it seems that all the Five Poison Sects members have died during the night.

\textit{Hmm, did I kill half of them?}

\textit{Come to think of it, they poisoned themselves with too much poison and died on their own, so it's no surprise that they would call themselves suicide squad.}

\textit{Now all I have to do was go to Jinping, check on the situation of the Five Poisons Sect Hall without the Five Poisons Sect, and wait for support from the Diancang Sect.}

\textit{But before that.}

\textit{I can't go on like this.}

In this era, soldiers always moved around with water.

In other words, if there were soldiers stationed somewhere, there had to be water flowing nearby.

Sure enough, there was a small stream flowing outside the open space.

\textit{Water! Water to wash myself!}

Qing, who had stripped off her clothes and was running toward it, suddenly stopped with a squeal.

\textit{I'd love to rush right in, but um, should I wash first?}

Normally, you have to wash yourself even before getting into a hot tub, so on the river she couldn't go in with poison all over her body.

She brought all the pots from the kitchen barracks, scooped up water, returned to the barracks, and poured it over herself to wash off the poison that had stuck to her body.

Qing, who was not usually neat, looked very cheerful as she rubbed her body.

Still, the feeling of the mud and sweat being washed away from her body was something that people who wash themselves regularly would never know.

\textit{This is really going to hurt…}

\textit{I'm going to wash it off later.}

After rinsing herself off, Qing finally ran into the stream.

The water level only reached her shins, sos he couldn't fully immerse herself, but she lay down on the pebbles at the bottom of the stream, and the water flowing over her body felt refreshing.

As she lay in the stream, which barely covered her torso, two large pieces of flesh rose above the surface like twin islands.

If Ximen Surin had seen this, she would have thought her diciple was completely insane. How could she expose herself in broad daylight if se wasn't crazy? It was a situation that deserved a barrage of nuclear noogies.

But right now, at this moment, Qing was feeling complete freedom in the wilderness.

If you like it, then it's a good thing, isn't it?

After enjoying the refreshing feeling, she realized, "Oh no, I don't have any clothes."

She couldn't put that ragged clothes back on, so she had no choice. There was no one around, so she decided to look for something she could quickly put on.

Qing searched through the military tents and found the cleanest clothes she could find and put them on.

Then, her stomach growling like a sacred fire, as if asking for breakfast, and Qing's mouth watered.

\textit{I have to go down to Jinping and order something delicious.  I'll ransack the inn today. You should know that this is a day when everything is completely emptied."}

\textit{Wait, money! I knew it.}

She had left most of her belongings at an inn in Gejiu, so she had only brought two gold coins for travel expenses.

The clothes she was wearing were already ragged, but now they were nothing more than pieces of rags that could hardly be called clothes.

Of course, she had no idea when or where she had lost the hanging money pouches.

She couldn't search the entire mountainside and tropical forest just to find it.

What should she do? Should she just eat the food in the military tent for breakfast, which would only be one meal, and then go to Jinping without a penny to her name? What about lunch? Dinner? Where would she sleep?

\textit{What should I do? Is it time for Flower Beggar to return?}

\textit{It would be fine if I were just observing the Five Poisons Sect without any Five Poisons Sect members, but-}

\textit{Zhuge is bringing Diancang Sect members with him, so I can't show up looking like beggars…}

\textit{What should I do?}

Then, suddenly, Qing's gaze was drawn to one spot.

The bodies of the Five Poisons Sect members were piled up like a mountain.

\textit{They said they would die avenging themselves, and they did, but they only managed to die.}

\textit{They didn't even achieve their revenge, but I guess the process was more important than the result.}

\textit{In any case, regardless of whether their wishes were fulfilled or not, I fulfilled their desire to die avenging themselves.}

\textit{Then I deserve to be rewarded.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

And so, Jinping!

Jinping County was a city surrounded by Dazhai Mountain on three sides, and it was also a developed city thanks to its location on the road to Tea Horse Road.

However, the streets were quite deserted.

She heard that the city was going through a difficult time due to a strange disease that had reduced the number of merchants.

"Oh, because of that damn smallpox, merchants don't even pass by these days, and I'm dying."

The waiter moaned.

Of course, waiters tend to be expressive in their work.

They moaned even when a mosquito bit them, and if you give them a few coins, they treat you like a benefactor.

It was an occupational hazard for these people to be overly dramatic.

However, with the inn so quiet, his lament was somewhat sincere.

So, he lingered around the hall, cleaning the table one more time for no reason.

The table in the hall was already piled high with empty dishes.

Qing had already eaten a hearty meal.

If there was a hell after death and they can look back on their lives, the members of the Five Poisons Sect would have had to watch their money feeding their enemy..

In any case, the waiters were hanging around for a reason.

With no other customers around, he was lingering nearby in case the big spender might open her money pouch again.

Qing poked him lightly.

"Don't Five Poisons Sect know about medicine? Even the good herbs from Mount Dazhai were kept by themselves…"

"Uwaaah! Customer, shhh."

The waiter hurriedly stopped Qing from speaking and looked around frantically.

However, it was between breakfast and lunch, an ambiguous time in the morning, and there weren't many guests to begin with, so no one was occupying the seats.

"You must be careful what you say. What if someone hears you?"

"Hmm. Is that all? Anyway, if they know poison well, they must know medicine well too. Is ther any talk about a cure or something?"

"That's-"

The waiter blinked unnaturally.

He wanted Qing to do something.

When Qing handed him a handful of coins, he cautiously looked around, and even though there was no one else around, he whispered carefully into Qing's ear.

"Actually, the warriors who collect payments haven't come for the past few days. The main gate was locked tight, and people were saying that a strange disease is spreading inside Five Poisons Sect."

Even though there were no guests, the whispering made it seem like Five Poisons Sect was a scary place.

However, it was just worthless information that was worth no more than a coin.

Well, that's because all the Five Poisons Sect warriors who used to collect the money were in heaven, or rather, in hell.

They locked the main gate because the inside was a Blood Cult den full of Blood Cult members.

How can they show those strange and suspicious monsters running around on four legs to others?

\textit{It seems like I need to go check it out first.}

\textit{But where should I start?}

Then, suddenly, Qing looked at the empty plates.

\textit{Right, the Blood Cult bastards have to eat to live, so there must be people who supply them with food.}

\textit{By looking at the amount of food they need, we can figure out how many Blood Cult members are in the Five Posions Sect headquarter.}

\textit{But the person who delivers the food could also be connected to the Blood Cult. Hmm, what should I do?}

\textit{For now, let's just scout them out.}

\textit{There was a minor altercation along the way, but that altercation led to the destruction of the Five Poisons Sect, which was an even more minor incident.}

\textit{More important than that iss to completely wipe out the Blood Cult.}

\textit{Even if the Diancang Sect steps in, we need to gather as much information as possible to minimize the damage.}

\textit{For now, let's take a look at what the Five Poisons Sect headquarters looks like.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Jinping County was a smaller town than it appeared.

The reason it looked big was because there were many warehouses that were not inhabited.

The high mountain range in the west was called Caotangpo, and it was said to be the best tea-growing region in Zhongyuan.

That's why there were so many warehouses for drying tea leaves.

And the main building of Five Poisons Sect was, well, big.

It was surrounded by a high wall about a meter thick, like a castle wall.

It looked like a fortress in the middle of the city.

The main gate was on the south side, and there were several small gates in the rest of the wall.

Among them, there were two gates that looked like they could be used to hide something.

They were side gates used by servants, but they had doors on both sides and were large enough for a cart to pass through, so they were easy to spot.

\textit{First, I need to see the delivery of the food ingredients.}

\textit{If I ask around and raise suspicion, the Blood Cult might find out, so I'll just kill some time at the teahouse.}

\textit{I planned to quietly follow the delivery man and find out who he was.}

"Excuse me, owner? I'd like some sweets, um, all the different kinds, please."

"Excuse me?"

"Hurry up."

How much time had passed as she sipped her tea and nibbled on sweets?

She decided to consider it lunch.

The shopkeeper, who had been anxious, became very cheerful after Qing paid her halfway through.

It was then that it happened.

Across the street was a restaurant, or rather, in Zhongyuan standarad it was just a cheap place to eat.

The clerk struggled to carry a large basin and poured its contents into a large container at the corner of the alley next to the restaurant.

Suddenly, memories of the past came flooding back to Qing.

Yes, when it was time to close, they would pour the food waste, or "cham" in military jargon, into a trash can next to the restaurant.

This was also the meal of the beggars.

Of course, it was like pie in the sky for the plague-ridden beggar.

If that beggar touched the trash can, the entire trash can would be contaminated.

Just looking at it would get her beaten up.

Still, if she were lucky and there were no other beggars around, she would quickly grab some food and run away.

Then she didn't have to fill her stomach with bugs and tree bark.

\textit{Back then, I was so happy with that bag of food waste.}

Just then, a young beggar ran up with a big smile on his face and scooped up a handful from the trash can with an old bag.

\textit{Yes, just like that. That's what made me happy.}

That was the moment.

"Hey, you! You plague-ridden brat!"

\textit{Huh?}

The young beggar jumped up in surprise, then immediately ran away.

Bang!

The young beggar who was running away tripped over someone's foot and rolled badly on the ground.

Judging by the clothes of the person who tripped him, it was probably one of the other beggars who was picking on him.

However, he had a sturdy club in his hand.

"You plague-ridden rat, you dare touching the elders' food again ? Didn't I tell you that if I caught you again, I'd beat you to a pulp? Ha, you don't seem to understand what I'm saying, do you? You should know you're going to lose today."

Qing's eyebrows twitched.

\textit{Wait, look at that brat talking like that? For some reason, it doesn't feel like someone else's problem. I can't help but get drawn into it.}

\begin{lstlisting}
The chapter title is a reference to a Japanese saying, '人を呪わば穴二つ'/ 'if you curse someone, there are two holes'. The modified version, 'Before embarking on a journey of revenge, dig two graves', often misattributed to Confucius.
\end{lstlisting}