\chapter{If You Want to Kill Someone, Prepare Two Graves (10)}

Qing scratched her cheek.

Before determining whether Jong's father, Jong, was truly a villain, there was something that needed to be clarified first.

"What is this? Didn't Lady Lee just say that she carries Jong's child in her womb? If they intend to eliminate Jong's offspring, why do they still carry that seed within themselves?"

It was a monologue.

A monologue that directed to no one.

To this, the magistrate exploded.

"You! Didn't you just confess that you carry Jong's child? Look now, this is all a scheme to pass the estate to your own children!"

The crowd began to murmur again.

'Oh. Is that right?'

'Isn't this just a common rebellion by a concubine? But what of the skeletons?'

'Well, is it unusual for a merchant to clean up people underfoot?

However, the undeniable fact was that the magistrate, who had rarely been seen since taking office, turned out to be a tremendous magistrate and chief constable.

Turns out he wasn't particularly uninterested in the affairs of the constabulary; he was quite sharp.

The magistrate's popularity was soaring.

"Th-that's…"

Lady Lee stammered.

She hadn't expected her weak words to bounce back at her, especially with the ruthless blades of a professional executioner aiming at her.

Even if she claimed falsehoods now, it wouldn't change the fact that she was pregnant. She clasped her belly as if protecting her child.

"Esteemed one. The father of that child is—"

"Dage!"

"It can't be helped. Since you will be embroiled in this web of guilt anyway, isn't it better to bear them than to be a sinner's child? Esteemed one, the child in the lady's womb is mine. I've shared my love with her."

"What!?"

The head manager made another shocking confession.

Even the magistrate seemed poised to leap up in surprise, and the venue erupted in a chorus of shocked murmurs.

However, as Qing observed the scene, she noted that amid the chaos, the servants of the Jong Trading Company appeared unperturbed.

If these little ones had a rough idea, then surely the servants wouldn't be clueless.

In truth, this was a flimsy incident.

Simply bringing a physician would have revealed the truth, as it was quite straightforward.

It wasn't that the head manager and Lady Lee were foolish.

It was merely an incidental occurrence, and when dealing with emergencies, flaws were bound to occur.

Nevertheless, this situation arose mainly because the members of the company had accepted it tacitly or even actively agreed upon it.

As they say, three people can create a tiger from nothing.

If dozens of individuals from the Jong Trading Company attempted to deceive, how could even the children remain unaware?

Yet the magistrate was exasperated.

\textit{For the Inspector to be present, in my jurisdiction of all places, and for such a heinous act to take place!}

"How could this be? Are you colluding to devour the trading company? How could such a dreadful occurrence happen…! I will have you all—"

"I would prefer a different resolution."

The magistrate, who was about to shout for a beheading, immediately clamped his mouth shut.

After all, whose words were those? How could he disregard the inspector's instructions?

Qing walked up beside the magistrate.

"I am truly impressed. Esteemed one, your brilliance has illuminated the dark secrets of this gruesome incident, truly a renowned magistrate like Po Hee-in!"

Po Hee-in, known as the famed magistrate and prime minister in Qing's hometown, was the ultimate detective.

Thus, relief washed over the magistrate's expression.

\textit{Thank goodness, the Inspector seemed to have a favorable view.}

"However, while I present my case, it was said that the law exists primarily to comfort the weak and wronged commoners, does it not?"

This was something the magistrate had never heard before.

From when did the law become about helping the weak and unjustly treated? It was utterly perplexing.

But now he understood.

What did it matter what he didn't know in the past? What mattered was that he knew it now.

\textit{From now on, the law, as per the Inspector's words, would exist to serve the weak and unjustly treated commoners.}

"Indeed, esteemed one, even if you are a martial artist, your words are truly just. So, what advice are you offering now? I will take it as my duty to heed the will of the common people."

"If a magistrate truly heeds the will of the common people, then he becomes a true symbol of a righteous magistrate, and such a magistrate committed to the welfare of the people is indeed a blessing from the heavens. Isn't that right, everyone?"

Despite suddenly becoming an esteemed magistrate, for some reason, the crowd appeared to be gleaming and drawn in, feeling as if the magistrate was indeed a brilliant magistrate!

"Since the owner of the estate has passed away, he cannot be held accountable for the estate's illegalities, and ideally, that responsibility should not fall the son."

In Zhongyuan, the principle of guilt by association was fundamental.

Originally, the utmost standard in Zhongyuan was officially filial piety. (Officially, at least, but in reality, the highest value among Zhongyuan people was gold.)

Hence, it's considered filial obedience for children to pay for their parents' sins, so it's natural for children to be held accountable for their parents' wrongdoings.

"However, the son had no involvement in the estate's matters, so to hold him accountable would indeed be harsh, and the most significant victims of the illegalities would be the children, wouldn't they?"

"Then what?"

Qing contemplated, and it seemed like this might actually be the right approach.

Given the circumstances, it appeared that Jong was indeed a heinous serial killer, and thus, the head manager bore no guilt for his murder.

If a villain dies due to his own evil deeds, then that's simply a natural death.

After all, what qualifications were needed to eliminate a bad guy?

Anyone can pick up trash.

Just because one's own space was filled with garbage and reeks doesn't mean they can't pick up trash.

Thus, concerning Jong's killing, Qing had no desire to pursue it as a crime.

But expelling the children was a different matter.

To force innocent children, unaware of anything, into the streets to die due to their father's sins, that act was practically attempted murder, clearly an action aimed at killing.

Was he trying to cut off the bloodline of a killer?

If Lady Lee hadn't been pregnant, it might have been somewhat credible, but given the current situation, no matter how one thought about it, it was a flimsy excuse.

Because expelling the kids would benefit his own child, creating a scenario where they would gain from it.

Even if such a sentiment existed, once personal gain was involved, purity was impossible.

As if one could see his smirk blooming, he was likely thinking, "Good deal, enrich my chaotic child along with the trading company," reveling in a feeling of having it all.

So it felt right to act accordingly.

"Then perhaps you should render a judgment upon them, regarding that boy?"

"Hm. Originally, this was to be resolved by the law, but upon hearing your words, they indeed seem quite reasonable. So, ahem, Jong's son, listen! As the head of the noble family, I shall respect your decision!"

At this, Jong Mun-woon, who had been standing in a daze, suddenly snapped his head up.

He looked at Qing as if he were a lost child, bewildered.

Qing shook her head gently.

It wasn't that she was going to defer the decision.

She couldn't make a decision regarding him.

After all, if the children had wanted to ask to take down the adulterous couple, or if they were totally uninvolved but had come to learn of the circumstances, then perhaps shouting for justice could have been justified.

But the children—while the younger one was still too young to think about such matters, the slightly older one had come of age.

No one could rob the victims of their right to avenge their unjust suffering.

"I, I…"

"Mun-woon? But I am still your mother, right? I plead, I beg you, please forgive us, okay?"

Lady Lee immediately clung to Jong Mun-woon's pants, wailing for forgiveness.

Jong Mun-woon gazed at her with a chilling look before turning to the head constable.

"Head constable, or uncle. Is that the truth? Was my father truly such a murderer? Was my grandfather as well?"

"…That was a form of insanity. The kind that only seems satisfied upon seeing blood—a terrible madness."

Madness meant mental illness.

What does that mean? If one had to describe it, perhaps it could be called a disease of slaughter? It felt oddly cool and familiar.

"I was originally a servant. I acquired him to clean up the results of that madness. By all rights, I should have died long ago to silence him, but I realized this and struggled to advance the estate. I made significant contributions to its expansion and was acknowledged for my utility, eventually becoming your father's right-hand man, thus taking on the role of a sworn brother at last."

The reason he had become the head constable and why he had to.

And the truth regarding his father.

Jong Mun-woon's lips trembled.

He barely managed to hold back the words, realizing he couldn't express himself and feeling choked as if he were out of breath.

At that moment, a gentle touch landed on his shoulder.

A cold yet comfortable warmth radiated from it.

Even without turning his head, he could tell who it was—Qing's gentle touch.