\chapter{If You Want to Kill Someone, Prepare Two Graves (3)}

"Uh, yes. Yes?"

"Hey, you little brat, why are you dressed like a beggar? There's a beggar in the making here. People have to work, you can't just play around and eat."

Qing grabbed the boy by the neck with one hand and lifted him high, walking slowly.

The boy was cowering, so Qing kept talking to him to ease his tension.

"Come on, let's have a hearty meal first. If you don't eat well when you're young, you won't grow tall. What do you like? Consider yourself lucky today. Just tell me. Boiled pork? Soup? Grilled meat? No, let's choose some meat first. What do you like: beef, pork, chicken, pigeon, or quail?"

"What? Um, then—"

"No, eat pork, pork. Pork is good for you and tastes good. Did you know that pork is the most delicious meat? I heard somewhere that pork is the only meat that is so delicious that it had to be banned."

"Um, Great Expert, wait a minute, let me say something…"

"Now, imagine this. You put it in broth and boil it vigorously, then you take it out and tap it lightly, and it shakes and trembles. When you cut it with a knife, the juices flow out and it has a white, shiny luster. When you put it in your mouth, you don't even have to chew it, it just melts in your mouth, and you don't have to be stingy, just grab three pieces and put them in your mouth and chew, and then add some white rice…"

Gulp. The boy swallowed loudly. And then he gulped again.

Just listening to her made it sound delicious.

The boy, who was listening to Qing's praise of the boiled pork as if he had lost his mind, suddenly looked up in surprise.

"Wait! Wait a minute!"

"Huh? Why? Oh, you don't like tender meat? Meat should have some chewiness? Ugh, you don't know how to eat. Meat should be tender, no matter what. You're still a kid, so you don't know what's delicious."

"No, that's not it—"

"It's just that I haven't been to a restaurant that makes it well. Hmm, but where is a good place in this neighborhood? Hey, you live in this neighborhood, you must know which restaurant is the best…"

"Brother! My brother is here!"

The boy couldn't get a word in edgewise as Qing kept talking, so he finally shouted.

Qing realized her mistake.

She tought the child was trying to refuse persistently because he felt embarrassed to beg for food and his pride was hurt, so he was trying to talk her out of it, or rather, he was scared of her.

But it seemed that it was his sense of responsibility as an older brother to feed his younger brother.

"Huh. You have a younger brother?"

"Yes, my brother is sick, so he needs to eat more to get better. Great Expert, I'm fine, so please take my brother…"

Qing remembered the boy desperately gathering the food scraps that had fallen on the ground even after he had fallen badly after tripping over his feet.

In such a dangerous situation, he should have run away, but instead he was desperately gathering food scraps.

So, it was a heartbreaking effort to feed his sick brother.

Even if he didn't eat the food scraps himself, he was determined to feed them to his sick brother.

Even though he was in danger, he had to feed his sick brother because he cared more about him than himself.

He was determined to somehow feed his sick brother the rotten and smelly food waste.

\textit{Hmm. I'm starting to feel a little moved.}

\textit{But since it's food waste, it's not really a heartwarming story. It's just trash…}

Well, where would a beggar be able to find decent food?

And he wasn't just any beggar, he was a beggar known as a plague bearer, which meant he was untouchable, even by other beggars, and couldn't even beg for food…

And this little kid would have known that from experience.

Food that was just thrown away, not hot but not yet spoiled, was the most popular meal for beggars, and just hanging around there trying to get some was a very risky move.

"Hey, kid, you're trying to look cool, aren't you? You weren't just feeding yourself, you were feeding someone else too. So what? Where's your brother? Which one is he? Come on, tell me."

The boy replied.

"Then, could you please put me down now?"

"Oh, right. It's so light, I didn't even realize I was holding you. You need to gain some weight. Kids need to be a little chubby."

"Kids? I'm not a kid…"

"What? Are you trying to tell me you're not a kid? Come on, the fact that you're saying you're not a kid is proof that you are. Real adults love it when people say they look like kids."

Children want to grow up as quickly as possible, but once they become adults, they want to be children again.

Isn't this the inevitable perception of aging that humans have, an essential contradiction and sadness?

In other words, insisting that you were not a child was tantamount to loudly confessing, 'I am a child!'

"Well, what do you say? Are you still going to insist that you're not a child?"

"… Ugh."

The boy turned his head away in exasperation.

\textit{Hmm, he's a fun kid to tease.}

Anyway, Qing follows the little beggar.

As they left the main road and headed further out into the suburbs, the streets become deserted.

But that didn't bother her.

According to what she had heard from the waiter, there were many warehouses in Jinping where tea leaves were fermented and stored.

This was a warehouse district, and he had said that there were no merchants around these days, so it was only natural that there were no people around.

Come to think of it, she was a little skeptical of the little beggar's judgment.

Beggars tended not to be very observant, but they were not completely oblivious.

Therefore, begging in front of people was the minimum level of observation they were capable of.

What if there was no one watching?

Then, only other beggars would know what they were really doing.

For starters, beggars eat people.

And yet, he hid his younger brother in such a deserted place?

He wouldn't have hidden only his younger brother, so he must have secretly set up a hideout in an empty warehouse somewhere.

In that case, it's a miracle that they haven't been eaten yet.

\textit{Hmm, I can't leave them like this.}

\textit{As a senior plague beggar, I must teach my junior plague beggars the rules of survival. Hmm, let's see…}

Rule of survival number one.

Give up on anything that people can eat.

Beggars were sensitive about food, so if people think the beggars don't covet their food, the beggars would get beaten less.

Instead, you need to think outside the box.

Start by questioning whether things that people say were inedible were actually edible, and then gradually expand your list of things you can eat.

\textit{Hmm. Come to think of it, this kid isn't like me, who can eat anything without getting sick, so this won't work.}

\textit{My rules for survival are more useless than I thought…}

\textit{And my first year as a martial artist…}

\textit{No matter how much I think about it, my first year as a martial artist seems like a complete waste of time.}

\textit{Still, I must have learned something. Hmm, something, something, something, even if it's just a little.}

Qing followed the boy beggar, trying hard to figure out how her first year as a martial artist had helped her in her life, what she has learned, and what meaning those difficult times had.

How long did she followed him?

Qing couldn't find any meaning in it, and the boy beggar arrived at the entrance of his hideout.

"Here. Come this way."

The boy beggar squeezed himself into a narrow space between two warehouses.

The boy was a little kid who looked to be about ten years old.

It was a narrow passageway where even a little kid had to turn sideways and walk sideways.

\textit{Hmm. This doesn't look good.}

Qing triesd anyway.

You won't know until you try.

You can't give up before you even try.

不爲也非不能也. Bu Wei Ye Fei Bu Neng Ye.

Not doing it does not mean you can't do it. These were the words of Mencius.

Don't give up before you even try.

\textit{Besides, I don't know about the sides or the top, but I'm skinny as a rail, so I'm sure I can squeeze through the front and back.}

\textit{This should be easy to get through…}

"Hmm, it's a little narrow, ugh…!"

Qing was stuck between the walls and groans.

She managed to squeeze herself in, but now her chest and hips were stuck, and it hurt.

Still, she had natural strength, and flesh can be pushed down somehow, so she managed to move forward little by little.

In fact, the words of famous ancestors in this world often contradict each other on the same subject.

'Don't bite off more than you can chew.'

In other words, 'Of course you have to try it to prove it actually works or not, you stupid woman.'

These were the words of the Zuo Zhuan, the primary commentary text of the Spring and Autumn Annals.

In simpler terms, don't even look at a tree you can't climb.

With all that flesh stuck to her body, isn't it foolish to try to crawl through such a narrow gap?

\textit{Ah, this is no good. It's impossible, completely impossible.}

Realizing what she was doing, Qing struggled and finally managed to crawl back outside.

"Hmm."

\textit{Come to think of it, the young beggar's judgment seems to be quite good.}

\textit{How many people can pass through such a narrow gap?}

\textit{Unless you're a skinny kid who can't eat, it's impossible.}

\textit{If I had to choose, the only adult who could pass through there would be Young Lady Murong.}

\textit{No, that's not right. Young Lady Murong was thin on top, but she has powerful legs, so she wouldn't be able to fit. Probably?}

\textit{That would be the perfect hiding place to hide from beggars.}

\textit{Even if a beggar managed to crawl in, they would be stuck and unable to move, so they could be easily repelled with a single stone.}

\textit{Using physical advantages, not bad.}

In fact, even though they were called plague beggars, the fact that they were still alive shows that they have excellent survival skills.

"Great Expert?"

Not seeing her follow, the little beggar must have been puzzled, because she heard his voice from the other side of the crack.

"Ouch, I can't get in because my chest and butt were stuck."

"…How can you say such an embarrassing thing?"

A surprisingly polite voice came back.

\textit{What is this? Is he a precocious kid?}

"Then, I'll take my brother out…"

"No, it's okay. Keep going. I'll catch up."

"Yes, but, that, um, you can't come because you're stuck."

"There's a way. Keep going. Keep going."

There was no need to squeeze through that narrow gap. If you can't go through the gap, just go over it, right?

Qing jumped up and landed lightly on the roof of the warehouse.

The carpenters who built the warehouse probably never imagined that the narrow gap between the warehouses would become a lifeline for a little beggar.

If they had built the walls without any gaps, fires would have spread easily, and the bricks would have become vulnerable to moisture from rain.

So they probably just built the walls close together, leaving only the minimum amount of space.

Thanks to that, the young beggar brothers were able to survive the vicious cannibalistic beggars. 

\textit{Hmm, maybe this will count as a good deed and increase their good karma?}

She chased him to the end of the long, narrow gap between the warehouses, and behind it, she saw that the warehouse was somewhat smaller.

Just big enough for one person? There was a hidden alleyway narrow enough for a broad-shouldered person to lie down in.

At the end of it, she could see a roof barely covered by an old tarp.

Qing landed lightly in the alley.

Perhaps because of the sound, a weak voice came from under the low tarp that reached down to the waist.

"Brother, are you here?"

"Yes, it's me. Ugh, the smell. You should empty the toilet regularly. Even if you don't have much, you should live cleanly."

Qing (a former plague beggar and former flower beggar) joked around.

"Huh, who are you?"

Qing bent down and looked inside the tent.

There was a little boy with a yellowish face.

He looked very frightened, so Qing smiled to reassure him, but then realized that he couldn't see her face.

"Me? I'm a physician. Your brother said you are sick. Let me check your pulse. Can you hold out your arm?"

"Are you a physician?"

The younger beggar asked, but still held out his wrist.

Underneath his oversized cotton clothes and tattered rags, his thin wrists were exposed, with only skin covering his bones.

"No, actually, I'm not a physician. I'm a quack."

"Huh."

His younger brother, the beggar, was startled and pulled his hand away.

But it was already too late.

"Come on, life is what you make it, and there is no escape. Since I've come this far, you have no choice but to have your pulse taken by a quack doctor. Hmm, what's this? It's nothing. It doesn't even hurt."

"Really? I'm not sick?"

"Of course. It's just because you haven't eaten enough. Just eat well and get some rest, and you'll be fine."

As expected, it was just malnutrition.

"Thank goodness…"

A slight smile appeared on the yellowish face of the beggar boy.

However, it was only momentary, and he quickly returned to his sad expression.

"But you said you're a quack. You can't trust quacks."

"Oh, you little rascal. A true master never admits to being a master. If someone calls themselves a quack, they must be a really great physician."

Qing thought of Lanzhong Daren.

Actually, even if it wasn't Lanzhong Daren, it would be the same.

Real rich people don't say they're rich, they just say they make enough for a living. Even painters, the really good ones, always say things like, 'I can't paint well, it's embarrassing,' even though they hang their amazing paintings everywhere.

"Hehe."

"Why, are you happy that you're getting better?"

His younger brother, the beggar, smiled shyly.

"When I get better, I can go out and help my brother. I'm just lying here all day."

"Ha, really. I'm speechless. This is such an obvious melodrama. Do you think I'm going to be moved by this? Oh, wait, I think I'm going to get something in my eye."

Qing carefully picked up the child with moist eyes.

"Now, let's go eat. You need to eat to get better. Unfortunately, you can't eat anything greasy. But you'll be fine in a few days."

Just then, he heard a noise behind him.

"Huh, Great Expert? How did you get here?"

"Well, masters always arrive first even if they leave late, don't they? And your brother just collapsed because he couldn't eat, so he'll get better if he eats well."

Just a moment ago, the master had said one thing, but now she was saying something completely different.

In Zhongyuan, they say that if a man says two different things, he should have his balls cut off.

Unfortunately, Qing had long since lost her manhood, so this saying did not apply to her.

"Ah…"

"Come on, get back outside. It's time to eat."

"What?"

Qing, holding his younger brother in his arms, flew up into the air without warning.

It was an anti-gravity jump, a technique of Yue Maiden Footwork.

After that, the older brother was left alone in the secret alley.

As he looked up at the spot where the little beggar had flown away and disappeared over the roof, a thought suddenly occurred to him.

\textit{If this is going to happen, there was no need to tell me to go ahead…}
