\chapter{Break through the door and head towards the stars (2)}

The cliffs of Jeolnakseong and Gangpaecheon are completely separated.

If a supreme warrior must die and offer his heart, then at least it shouldn't be the heart of our Jeolnakseong/Gangpaecheon warrior!

The two factions' thoughts were in agreement.

Even if it was just at the peak of its unmanned state, it would be possible to somehow persuade it with words.

But what about the climax?

It was also a key force within the sect.

When young, isn't he a treasure of the school that must be nurtured, and when old, isn't he a great veteran who has experienced all kinds of hardships?

Dark night.

The torches flicker, casting shadows that swirl and sway.

For a moment, the eyes of the two Sapas anxiously estimate each other's numbers.

The ten great natures of the apostles are five thousand and five stars.

In terms of scale, Gangpaecheon, which was one of the three Gangs among the five thousand, was a much more powerful sect than Jeolnakseong.

However, in terms of current power, it's a landslide victory for Jeolnakseong, which was personally visited by the leader of the enemy.

The Gangpaecheon warriors move slowly, trying to hide their retreat route.

If they rush in to kill them because they are at a disadvantage right now, the search party will inevitably lose, unlike the entire sect's power.

So, get ready to run away.

Junki-chung's eyes shake wildly.

Should I hit it now? Or not?

But was there any guarantee that you will catch a top-tier expert who runs away in the middle of the night, ignoring the road?

What if I miss it like that?

You don't have the ability to handle Kang Pae-cheon's revenge?

But if you fight, you will win right away.

Aftereffects? After obtaining the absorption magic, I wonder if I'll be afraid of the likes of Kang Pae-cheon.

But Jun-gi-chung held on tight.

It was a strange organ that requires the heart of an unmanned person from the very beginning.

I wonder if there are any traps inside?

And how spacious was the inside?

Let's say you go in right away.

If you step on a trap, won't you end up creating a new path for those who come later?

Moreover, since the fireworks were so splendid, even those who had been watching from outside the mountain would all rush up.

Meanwhile, the Gangpaecheon warriors took up positions with the retreat route flanking them.

It was a silent signal that they will run away if attacked.

It was a reorganization that was carried out purely by observation, without anyone in Gangpaecheon directing it.

Wouldn't it be great if they could communicate with each other so that they could ensure their safety?

"Look, Cheon Seung-in. Now was not the time for us to fight. Didn't you come up here after seeing the flames? All the rabble will come, and we can't hand over our magic to them, can we?"

"Then? Is the heart of transcendence something that the Holy One will prepare?"

Yuk Cheon-seung, who was leading the search party on behalf of the young master, answered.

Jun-gi-chung shakes his head at him.

"Even among the rabble, there's bound to be at least one exceptional individual. If the pillars of our Apostles join forces, wouldn't it be difficult to secure just one?"

That's not wrong, but I wonder?

The six thousand monks who condemned the blood sect and then made a big fuss like a fool during the praise time for the writing.

But, I did that because the handwriting was really good.

To recognize letters, you need to develop your eye by looking at many letters, and those who can read letters like this have read a lot of text.

Six thousand heads are rolling around.

If you give in right now, you will lose.

But Jeolnaksung can never fight.

The damage to Jeolnakseong will also be great, and after that, the castle lord will not be able to handle the nonsense he just spoke of.

but?

Are they going to share their magic with us?

No.

Even if you take the magic to Gangpaecheon in the first place, will he teach you that peerless divine technique?

He could not even protect the son of God, the successor of Kang Pae-cheon.

No matter how fair and impartial the leader is, what would his father's feelings be like?

Even Kang Pae-cheonju and Kang Chu-on were far from fair people to begin with.

Even if you offer up your magic power, it's obvious that you'll end up like a loser.

In that case… … .

Yuk Cheon-seung swallowed his sinister feelings.

"Very well. We cannot allow the world's greatest treasures to be seized by a rabble. So, do you have any good plan?"

"Among the ronin and the various sect thugs, there must be a super-talented one. Grab one and open the door, and push the rest into the passageway first, and they'll use their bodies to break the trap."

"Oh, the Holy One has come up with a truly wonderful strategy."

So the two Sapas face each other, slightly relaxed, but still with their hands on the hilts of their swords.

That's only natural.

We did say that we should join forces.

But how should we divide the magic?

It was not a sacred book that we can share with each other by writing it down and being friendly.

In the end, it will end up being a fight over emergency supplies.

It was during that time.

-\#\# \#\#\# \#\#\#\#\# \#… …

It's like a whisper, a mumbling sound with no pitch, with a very unfamiliar pronunciation.

It's not as if the skill of a six-way battle was whispering from all directions.

Still, the sound coming from one direction was clear to everyone.

It means that the internal energy was no ordinary one.

Everyone's eyes were turned to the protruding protrusion on the downhill slope.

Finally, one monk appears in the light, looking very skinny and grotesque.

It looks like a mummy, with no muscle in its entire body and just skin over bones.

However, the eyes shining through the hollow eye sockets were fierce and had an intimidating power that made everyone flinch.

For now, we have decided to join forces.

The highest among them was Jeolnaksungjon, so Junkichung stepped forward and took the lottery.

"What kind of person was the deceased?"

The monk glared at him and spoke in a hoarse voice, as if filled with sand.

"Cheoncheonni……"

"Huh? What do you mean, slow down?"

"Central Korean, difficult. It's me. I'll be fine."

"Amukhaprap!" "Monster!" "Amukhaprap!"

The monster Amukhaprap.

Usually, the term 'goe' refers to a title given to a strange person.

When I say something was strange, I don't mean it means you have a quirky personality.

This means that he was inconsistent in his actions. Sometimes he acts like a madman, and sometimes he acts like a knight. He was neither here nor there, so he was a strange person, a monster.

That was to say, it's unpredictable.

"Why was the Monk involved in the affairs of Zhongyuan-"

Amukhaprap raises his hand and cuts off Junkichung's words.

And then he says it again.

"Slowly. The people of Zhongyuan believe that everyone speaks the Zhongyuan language. \#\#\#, your mother does not exist."

Some unintelligible words were mixed in along the way.

But everyone understands that it's a curse word, even though they don't know what it's.

The content was insulting, but the pronunciation was awkward, so it doesn't really hit home.

"I have come to seek the Great Absorption Law. Please step aside. My martial arts are extremely fierce."

Junki-chung thinks about it for a moment.

Should I get rid of that old bastard of the chief now?

I glanced at Yuk Cheon-seung, and he nodded and matched the signal.

Jun Ki-chung gave him three fingers.

And two, one.

It was just as the last finger was about to fold.

Todok. The sound of something light settling.

But what actually landed was a lump of flesh that could easily weigh two hundred and fifty pounds.

A ladder that's incredibly tall compared to his small stature.

The face also gained weight, the facial features were concentrated in the center, and the torso was rounded like a swollen pig's urinal.

It's a sight that no one will ever forget once they see it, so it's easy to recognize.

The people of Zhongyuan called it Povidone because it looked like a piglet with a plump body and could fly.

He was a master called Povidone Jang So-nam.

"There are already a lot of passengers."

"Povidone!" "Povidone!" "The world was yours!"

"Yes, it's Povidon, the one in charge of pigs among the Cheonhaorang. Kekeke, Gangpaecheon and Jeolnaksung? And there's a lama monk there? Why, when you're already great martial artists, do you really need to have them all? Why don't you give up your magical skills to a homeless wanderer in the martial arts world?"

"Do you dare to interfere with the events of the Ten Great Apostles?"

But Povidone calmly opens his ears.

However, his arms are also plump and chubby, so even just picking his ears looks like it takes a lot of strength.

"Honestly, if I could just get the absorption magic, I could take a big place in the Apostolic League and make a fuss, so what's the big deal about a little interference?"

"What? Can you take responsibility for what you just said?"

"Aren't you being too harsh on these homeless wanderers? Isn't that right?"

"Yes, yes. You are right."

There was a new type that emerges from the mountain path.

He had long steel claws on both hands, and in the martial arts world, he was known as a magical weapon called an iron claw.

There was a nickname that everyone who thought of women who used iron wire thought of: Joayo Lee Hye-hye.

And Lee Hye-hye was also famous for her three loyal followers.

As expected, three young men followed behind her, surrounding her from the left, right, and rear as if to protect her.

"Who was this, Joayo? Did you also come to find that evil magician?"

"Of course. Then why don't you look for it? It's my lifelong dream to learn a proper new technique."

"Isn't something like the Palcheol Ajo enough of a new skill?"

"Oh, my, why are you doing that? You already know everything. Are you satisfied with the Six Treasures of Diamonds, Povidone?"

Those who use strange weapons or strange martial arts are especially thirsty for these divine skills.

It's called Gimun Weaponry because it sounds good.

If you take away the one advantage that makes it difficult to deal with because it's unfamiliar, isn't it actually a flawed weapon?

If it was a really good weapon, you and I would all have used it together, like a sword or a knife.

The same goes for bizarre martial arts.

Yukbo Geumgang Gong was a unique martial art that increases the body's fat and provides powerful defensive power.

But if that were truly efficient, then everyone in the martial arts world would have gained so much weight that they couldn't even wipe their own butts, so why would they be so lean and slender?

If you use such flawed weapons and martial arts, you can still become famous?

As a joke, if you had learned the new technique from the beginning, wouldn't the landscape of the top ten masters in the world have changed?

So, they have no choice but to thirst for new powers.

Junki-chung gritted his teeth inwardly.

Of all people! This little pig! Here!

The term "Cheonhaorang" refers to the five best masters among the ronin.

Of course, there are quite a few ronin who don't reveal themselves.

There may be better experts than that.

He was a very active and respected ronin among the ronin.

Each and every one of them was qualified to represent the ronin.

If Povidone gathers the ronin to his side, the plan to capture one of the super-climaxes and push through the door will turn out to be truly sinister.

And so was the povidone's trick.

So, as they came up and took their places, they saw each other and it was a three-way battle between the Heretic Alliance members, the ronin, and the ambiguous Maduna and unknown guests who were neither here nor there with the old monk in front.

And as the number of people increases, an eerie and murderous atmosphere gradually fills the room.

One of the peaks must die.

That way the door will open.

It was right in the middle of this war of nerves that the Qing party arrived at the West Gate.

It was a quick hike, even though we left late because we had to prepare our disguise.

It was a beautiful result created by the combination of the map in Tian Yuxue's head and Qing's transcendent night vision.

The area in front of the stone gate was already divided into three groups.

One side was the Sado-ryeon guys.

But what about the rest?

At that time, Tian Yuxue took the lead and took a seat on one side.

Others, Madu and anonymous guests were standing in line.

"Master? Am I in the right place? It seems like there are some bad guys all over the place. Does anyone know?"

'It's the shape of a pot's legs, so in times like this, shouldn't you stick with the weakest side?'

The shape of the cauldron refers to the famous Zhuge Liang's slightly less famous plan to divide the world into three.

Of course, the originator of the Three Kingdoms Divide was an old man named Goecheol, but if it were unfair, he should have been more famous than Zhuge Liang. What a pity.

The large cauldron has three legs.

Because with three legs, it can stay in place without shaking no matter how uneven or slanted the terrain is.

If it had four legs, it would inevitably rattle on uneven terrain, and if it had two legs, it wouldn't be able to stand.

So, for now, let's stick to the weakest side and watch how things turn out.

Wouldn't it be the other groups, such as the guitar, which are already short on numbers?

It was a strange reaction, with the enemy feeling reassured and at the same time wary as five people joined in.

So I saw the Qing turn around.

A supremely passionate heart to open the stone gate?

Otherwise it will collapse?

"Huh. They say it's the tomb of the Absorbing Demon, but the entrance itself was incredibly sinister. Hmm."

-It's a bit shabby, but I think I should change sides.

Tian Yuxue sends a message.

Qing answers him.

-why!!!

At that, Tian Yuxue's expression suddenly crumpled.

Not only Tian Yuxue, but also the unmanned people within a small cone around Tian Yuxue looked at Qing with a frown.

This was why Qing does not use the phonetic alphabet very well.

I can't control my vocal volume at all.

"Hey, just come here and whisper. We'll have to open the door first to get in and eliminate the magic absorption or something. This looks like the easiest way. Let's go with the ronin side."

But Qing doesn't move at all.

I just gently touch the fake flesh attached to my chin.

-why?

Qing whispered in the master's ear.

-If the entrance collapses, won't no one be able to get in?

-But then we can't go in either?

-Why are we going in?

-Well, we have to get rid of that damned Demonic Art from the world… ah.

Qing smiled brightly at him.