\chapter{Break through the door and head towards the stars (4)}

Meanwhile, the technicians of the Blood Offering unit who were eavesdropping on the situation going on inside the stone chamber were dumbfounded.

As a true practitioner of the organ-generating world, I have never once heard the nickname "Organ-wang-jon-sin-je."

The funny name Da Yeoreum was the same.

But I watched the scene nervously, wondering if it might be a fake name.

Well then, wouldn't it be quite a sight?

Even the most basic of examining the organs was completely useless.

What on earth do you think will happen when you keep hitting, groping, and applying force?

Since ancient times, to understand the origins of an organ, one must first dig into its surroundings, examine its core functions, and then carefully approach it.

He seems to be a pseudo-institutional engineer who has read a few books somewhere, and I wonder if he was trying to make a big profit now.

Now that I think about it, it's quite annoying.

It's so painful to see someone impersonating the master of the organ, and to see them impersonating someone and earning gold.

The Blood Cult technician looks at the side wall with a serious look, or rather, at the rope that says "Destroy Passage".

Cut that out, okay?

Even if we exclude the West Gate, the East Gate, South Gate, and North Gate remain, so it would be good to tear down one of them to properly teach that swindler a lesson.

But I'm worried about the blood, sweat, and tears of my colleagues in the passage.

Isn't this a masterpiece of the Blood Offering group that was created with sweat and toil for over twenty years?

Each trap has been built over many years of effort to reach the emergency room.

If we destroy the passage, it would be like wasting all the twenty years of development work that the West Gate has put into it.

So what?

Even though it's dirty, lethal, and disgusting, I have no choice but to endure it.

The blue one keeps making noises.

"Hmm," "Oh," "I see."

"Ah. You're coming out like this? I can't lose."

I thought to myself.

Miss, what was this? I don't understand a thing.

What should I touch to make it collapse?

No, doesn't that make no sense in the first place?

The door will open only if you set your heart to the highest specs?

Could it be that someone was secretly watching from behind and was manipulating the heart of the ultimate unmanned being to open it?

Hey, how could that be?

To have a video surveillance system in the central region.

If he didn't have clairvoyance, he would have to have eye holes, and then he would have to be able to sense human presence with his superhuman hearing.

But there's nothing like that.

Or maybe there's a secret inside the hole where the heart was placed.

Even if you sweep with Qing's sharp and sensitive sense, there was not even a tiny hole, let alone any device.

What the heck was the principle?

Qing thinks it's at most about weight?

Perhaps I underestimated the power of Zhongyuan' organs too much.

Well, it's a world where people can shoot rays, fly through the sky, shoot starlight, and split cliffs.

Hmm. I really don't know.

Qing thinks so and shouts.

"Well, the mystery has been solved!"

Everyone's eyes are focused on Qing.

Qing asks, putting his hand on his waist as if he was smirking.

"Everyone. The door opens only when you raise your heart to the highest level. Isn't that strange?"

"what-"

"What does that mean? I'm very curious. Please give me your teachings immediately."

Jun Ki-chung's words were interrupted by a monster.

Qing doesn't care who answers, he just says whatever comes to his mouth.

"The results of this investigation by the King of Organs-"

"Look here, young lady. Wasn't it the King of Organs' Reign?"

Povidone was causing trouble.

Qing frowned at him.

"Miss. Either way, if you get four, it's the same. Are you going to keep interrupting me? Should I just return the gold ingot and go home?"

"No, that's not it……"

"Usually, these kinds of organ transplants measure the weight and shape of the object being placed. But what about the heart? Do you think the heart of that plump old man over there and that skeletal monk are the same size?"

"It's so generous!"

Povidone jumped.

But apart from that, the audience looks back and forth between Povidone and the monster and makes expressions as if they have realized something.

The weight difference was probably five times, so how can their hearts be the same size?

Qing nods at that expression and says.

"Yes, that's right. Their hearts are the same size."

"……?"

There are not many people in Zhongyuan who have seen as many hearts as Qing.

From experience, the size of the heart was generally similar between men and women, with only a slight difference.

but.

"By the way, did you know that the heart also has scales? A wealthy man might have a lot of scales attached to it. But their hearts are probably about the same size, right?"

"So, what's the point?"

"Now. Listen. Let's say we're going to put the heart on. How should we do it? Should we remove the scaffolding and clean it? Or should we exsanguinate it and drain the blood? How much of the large blood vessels attached to the heart should we leave? What about freshness? How long ago was a heart allowed? Is it okay if it's half-decayed? What about contamination? Is a heart from a corpse killed by poisoning acceptable or not?"

"Huh? Now that I hear it."

Now that I hear it, it sounds plausible.

Even the Qing themselves say, "Doesn't this make sense?"

From the beginning, he only asked us to offer our hearts, but there was no mention of how to offer them.

And in the climax, what kind of heart flows with blood instead of energy?

After pulling it out, it was the same heart that couldn't even be distinguished.

Some people who have been exposed to the organs understand even more.

Why are there so many precautions and difficult operations for things like water-boiling machines and arrow traps that don't have any special functions?

"So, my conclusion was this was a complete lie! I'll stake my grandfather's honor on the fact that putting this in, whether it's the heart of a supremely unmanned being or something else, will have no effect."

People tilt their heads at him again.

If you're going to risk your honor, why risk your grandfather's?

So if I'm wrong, will my grandfather's reputation be ruined?

But Zhongyuan was a world ruled (or pretended to ruled) by filial piety.

It seems like putting my grandfather's honor on the line carries more weight than putting my own honor on the line.

So you're selling your grandfather?

Isn't this just a horo year?

Then the monster starts to complain.

"I don't understand. Then why was it engraved like that?"

"Um…. Just fight each other and kill each other?"

"Huh!" "Oh no!" "That can't be!"

It was a persuasive power that left me speechless.

Everyone's eyes widen at once.

"\#\#. Those Zhongyuan guys are truly devoid of parents. It's truly unbelievable. Even the devil would be impressed by the character of those Zhongyuan guys."

The Zhongyuan men glared at the barbarian bastard, but the monster monk paid no attention.

That was when.

Junki-chung shoots a sharp gaze.

"So, what's the conclusion?"

"I told you it's no use putting your heart into it?"

"Other than that. So how do I open the door?"

All eyes in the room were focused on him.

Come to think of it, it doesn't really matter whether the request to put in your heart was a threat or not.

How to open the door.

Qing knocks on the stone door.

"There's a way. Just look."

Qing picks up a stone and draws a mark on the stone gate, leaving a mark.

The line drawn in this way creates a square large enough for a person to pass through.

"This was the very space where the internal organs are empty, literally empty. I tapped on it and found out. This was the ultimate skill that only the King of Organs can master."

It was a nickname that changed every time he spoke.

Povidone wondered if one of the four was missing, but she thought that talking to her would only harm her, so she just kept her mouth shut.

"so?"

"What's that? A sword? You can cut steel with that, old man. Then, wouldn't it be easier to cut stone? Just cut it like this. That's it."

"what?"

"If you can't open the door, why don't you just break it in?"

It was a clear answer that was enough to elicit admiration.

If you can't open the door, break through it!

A truly Western-style idea that could change the worldview!

It was an idea that anyone could do, like someone making an egg stand on end, but no one could do.

"Have you ever seen such a crazy bitch!"

The Blood Offering technician who was listening was so shocked that he ended up shouting.

There was even a warning written on the door, big enough to say that it would collapse if you forced it open, but you insisted on cutting the door open?

The problem is, it actually works.

It's just a thick rock, so if you cut it with a hammer and dig it out, a hole will inevitably be made.

"No, no. Who would listen to a crazy woman like that? There's even a sign that says not to force it open."

The Blood Offering technician muttered something like that and started gnawing on his fingernails.

Fortunately, the generous old man, Povidone, picked a fight with Qing.

"Look, doesn't it say over there that it will collapse if you force it open? Is that okay?"

"Usually, if you force it open, the door will receive that much shock, right? Engines usually operate with that kind of shock. You, sir, can even split metal like tofu. So, there's no shock involved?"

"Hmm?"

"Even the designer probably never envisioned cutting the stone in that manner. At best, they probably thought they could strike it with a hammer or drill a hole to use a firearm."

It's strangely convincing.

"Okay. Well, I've done everything I had to do. You'll have to break the door yourself, right, sir?"

"What? Are you telling me to break through?"

"Hey, then do you also charge for the door break-in?"

The price of breaking a door.

Even the experts flinch at that.

Wasn't it Jeolnakseong who had the excuse to control the entrance anyway?

We can't let another person pay the price of breaking in at a time like this.

"There are so many experts here, how could they possibly cause such trouble to you, sir? This Povidone will help you."

"You too have the ability."

The Blood Offering technicians are crazy and going wild.

These crazy guys are really trying to break through the door!

So what?

He opens the lid of the emergency door, puts his mouth on it, and shouts urgently.

"Master, we're in trouble! Some ignorant bastards are trying to break through the west gate!"

The answer he received was firm.

-Then bring it down. Did the southeast and northeast gates collapse?

You're saying there's only one entrance?

Then the Blood Offering technician draws his sword.

The hardships of the past twenty years flash through the mind of the technician who flashed his sword.

The young me sighed in despair, wondering when on earth I would ever dig this rock mountain.

Still, there were rewarding moments when I felt that human power was conquering nature as I gradually opened up new paths.

Comrades who collapsed several times along the way and were lost each time.

The joy of overcoming such sacrifices and finally completing it, with tears in our eyes, hugging each other and jumping around.

And more recently, the horrific experience of wearing a breathable leather jacket and scooping out water and digging out drains.

All that effort, all that pain, all that sorrow, all that joy, all that achievement, all that goes down the drain with one stroke of the sword.

The Blood Offering technician's arms are trembling.

Tears welled up before I knew it, and they flowed down my chin.

What on earth were my years like?

Where on earth have all the efforts I've made so far, all the comrades who have passed away, and my youth gone?

But it's all for the sake of the grand scheme.

To burn down this rotten world.

And finally, the technician's arm moves.
