\chapter{Break through the door and head towards the stars (1)}

The leader of the Blood Cult's Blood Offering Corp, Guisan Manbak, Amharyong, stood at a crossroads of great decision.

The original purpose of the Blood Lantern Clan's Fisherman's Journey was to gather the righteous and evil factions together, instigate and fan the flames of conflict, and escalate it to the point of a war between the righteous and evil factions.

But the rumor was just beginning to spread among the political bastards.

As was the case with any coalition, the decision-making process takes quite some time.

Even if I wait, how long will it last?

There, the Sapa guys fight each other.

If things continue like this, it will likely escalate into a civil war rather than a war of attrition.

Of course, there was no official history in the suppression of the Blood Cult.

Either way, if the number of unmanned units decreases, it's definitely beneficial to the Blood Cult.

But what if a big gain turns into a small gain due to someone's interference?

Still, it's not easy to just let it go, saying that a gain was a gain.

There was a story that even in the hometown of Qing, there was a story that talks about the difference between those who succeed and those who fail.

If you buy something that costs one nyang and sell it for ten nyang, you make a profit of nine nyang.

Now, if you buy something that costs one nyang and sell it for nine nyang, how much profit did you make?

It was said that the person who fails gains eight nyang.

But successful people say that they have lost one nyang.

This means that the jeweler ended up losing money by selling an item that could have been sold for ten nyang for nine nyang.

Of course, there are also stories that say the exact opposite.

They say that those who see that one nyang as a loss will fail, and those who focus on making eight nyang will succeed.

Why do the same story lead to completely opposite conclusions?

Because the content of these self-help? development? books can be anything you want.

Because it's important for the listener to feel satisfied that they've read a really good book and have become a better person.

The authors said that the reason they worked so hard and failed so many times and finally succeeded was not because of their parents' support, but because of the great God who never gave up, and that this was the reason they were able to make money while bragging about themselves all the time.

Amharong was a person who focuses on the loss of one nyang, but he was not the type of person who gets so caught up in it that he lets the loss grow to two or three nyang.

"Open the four doors."

"Huh? You're already talking about this, even though the political bastards haven't even gotten involved yet?"

"The absorption magic will only fight if it falls into the hands of the Sapa. Even if it falls into the hands of the Jeongpa, the ten generations of the Gupailbang will probably just burn it to death."

The Sapa guys are crazy about the magic of absorption.

If you can practice it for a long time, wouldn't it be the best magic that can make you the best in the world and the best magician in the world?

The Sapas lacked the rigorous study that could be called divine skill.

So, whether it's magic or something else, I'm going to try to get my hands on it and learn it.

But the prestigious political factions have ample new power.

Since it's safe and has a powerful new skill, there was no reason to risk the side effect of going crazy like Saljungsal.

It's obvious that they'd rather burn it down than cause a huge controversy.

In Qing's hometown, this was sometimes expressed as kicking away the ladder.

The ruling party, which already had a solid foundation, didn't need the magic of absorption, so it was a much better decision to erase them from the world forever rather than have someone learn it and challenge them.

"If the Jeongpa bastards rush in like this, won't the Sapa bastards be swept away? So, what can we do if we want to pretend that the Sapa bastards have taken over the absorption magic?"

Kyoto Samgul, a clever rabbit digs three holes, was an idiom that means a clever rabbit digs three holes.

A single oyster. A large sword fight between the Jeongpa and Sapa near Mount Lao causes blood to flow.

Oysters. But even if the clash fails, it will cause a major clash between the factions that are trying to counter the Sapa's absorption magic.

What if even that fails?

Then, the responsibility was shifted to the leader of the Shibyeongdan, Eon Yeon-yeong, who interfered with others' plans and forced them to proceed.

That's three oysters!

Clever rabbit! Who was that!

It's me! Guisan Manbak! Who was Guisan Manbak?

It's me! Dark Dragon!

The dark dragon shrugs his shoulders, intoxicated by his own cleverness.

However, since it's a scene I have always seen, I am not particularly moved, and only suddenly have other questions.

"Then, I will open the four-way door."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It was a dark night.

Suddenly, with a faint beeping sound, a flame flew up with its tail hanging down.

pop!

A splendid display of fireworks lights up the sky.

And then a little later.

Beep, beep!

And then again after a while.

Beep, beep!

Fireworks at an untimely hour of the night.

People who were startled by the explosion ran out wondering what was going on, but stopped in their tracks as the flames slowly rose one by one, staring blankly at the night sky.

Aren't fireworks an expensive spectacle that can only be seen in each city during the Lunar New Year?

But why do you shoot one or two shots at a time?

Dozens of shells would explode simultaneously, filling the sky with sparks and making for a spectacular sight.

Afterwards, intermittent fireworks continued leisurely.

Should I try it? Two or three steps per day?

However, the people of Zhongyuan, who are always short of things to see, find it enjoyable and continue to gaze at the dark night sky with their necks stretched out.

Even the common people wake up their sleeping families and call them to look up at the sky.

Would the martial artists just sleep soundly in this commotion, wondering if a fire had broken out in a guard's house?

The martial artists who came to the Absorbing Magical Arts with their own unique aspirations also jumped out at this precious spectacle and looked up at the sky.

Suddenly, dozens of fireballs shoot out at once, beautifully decorating the sky above the distant Mount Lao Mountain with a multi-colored fireworks display.

"Oh……!"

The commonerss cheered.

Well, who wouldn't felt fun looking up fireworks?

My body was thrilled by the fireworks exploding one by one, and now the spectacle has finally unfolded.

The martial artists' faces harden.

Fireworks are rising from the mountain?

Fireworks rise from the mountain?

In this situation, some fools thought.

Why are fireworks being shot from Mount Lao? Who was shooting them?

But the majority of martial artists were people who at least had brains.

Something big happened in Mount Lao!

And isn't there a hidden magic absorber and a sacred treasure in Mount Lao?

So, those with impatient tempers took action immediately.

In their hands were lanterns, torches, lanterns, and even candles.

How on earth can I overcome this dark night with just one candle?

It was a characteristic of people who were shallow-minded but had excellent action skills.

They act first, but then, because they are not prepared, problems inevitably arise, and then they end up taking a long detour.

Still, it would be a bit premature to call those who brought candles stupid.

Because there were some who ran away empty-handed.

This was a characteristic of people who have no thoughts at all but are excellent at taking action.

For example, Qing.

"Let's go right now!"

"Oh, was it finally time to check the achievements of this double-edged sword?"

And the Grand Duke of Nan-gong Family who uses a double-edged sword.

"You guys. Don't you know how scary the night is? Are you trying to run out right now? It's so dark."

Fortunately, there was a big thief with common sense and manners in the group.

"Huh? It's dark?"

But Qing feels wronged.

It's a rare moonlit night.

Because with Qing's superhuman vision, he could see and distinguish the outlines of objects.

Thoughts can be replaced by a sufficiently trained body.

Even if there was no thought, the transcendental body can fill that absence.

So, the battle of incompetence between Qing and Nan-gong Shencai could be said to be a victory for Qing, who at least had the means to overcome it.

"And you plan on going out like that? Are you going to shout that the Heavenly Sword was here?"

"oh."

Anyway, there, there. Fifty paces are better than a hundred.

Qing's skin was also superhuman, so it doesn't even allow a small pimple to appear on something like a barely glued prosthesis.

But the group was not like that, and Qing also doesn't want to sleep with something on his face, so he just goes bare-faced.

So, first of all, disguise.

Wake up the messenger in the middle of the night to buy oil and bring plenty of torches and lanterns.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

What do Sapa and Hongmogui (white people) have in common?

Correct, after massacring the natives and taking over the village, he feels very proud and satisfied.

These are the Sapas who, at the end of the massacre, were occupying only a small village.

Of course, it could be said that it was a great bridgehead strategically, as it was a good location to set up a base while others were going down the mountain or sleeping in the rain.

They too were woken up by fireworks in the middle of the night.

At first, the Sapas thought it was a signal that something had been discovered, but their faces hardened as the flames continued to rise.

"What are you doing!? Prepare to search immediately!"

In that moment of great ambition, we all mobilized and climbed the mountain, following the flames.

And at the end, the search party discovered a huge stone gate that they had never seen before.

"What? You missed that stone gate so openly? Who are those guys who searched this area?"

"Never before! Really!"

"So, the door suddenly popped out of the ground? Why don't you bang your head in right now?"

The kids who searched this area are being treated unfairly.

How could I have passed by such a stone gate without my eyes being dazzled?

Rather, it's this side that's shocked, but it's so unfair and sad that they are hitting me in the head with it.

Next to the stone gate was a round ornament the size of a bean, seemingly carved from crystal.

If you can look behind the ornament, you will find a mercury mirror placed inside.

If you place the mercury mirror and go up at right angles to the holes and crystals placed here and there, and then go up to the end of the mercury mirror again several times in the shape of a "gi" (己), you will come face to face with the pupil watching outside.

A technician belonging to the Blood Cult's Blood Corps bursts into a vile laughter when he sees the Sapa warriors with their heads stuck outside the gate.

The stone gate was so elaborately camouflaged that the Sapa men, who had been searching the vast area roughly, could not have found it.

But it's funny how that tall guy keeps going on and on about who's responsible, and it makes me laugh just thinking about those Sapa guys who are so innocent with their heads down.

Two ropes are pulled taut and stretched to the floor next to the blood cult member who was looking outside as if he was enjoying the world.

The name tags written next to them.

"Open the passage" "Destroy the passage"

The moment you cut this line, a strange mechanism will activate, causing the stone gate to open or the passage to be destroyed, making it impossible to enter.

But the writing on the stone gate outside was different.

"Shingajimyo, West Gate"

"Offer your unmanned heart, transcending your own limitations, to this offering. Then it will open."

"If you try to force open the stone gate, the passage will collapse and you will never be able to enter."

And underneath it, as if by magic, there was a perfectly square, sunken hole.

It was obvious to anyone who looks at it where the blood donation is.

In fact, it's a strangely kind piece of writing.

Where was this? Shingajimyo.

Is this the only entrance? Can't you see the west gate? If there's only one entrance, would it be the west gate?

How do I open it? Heart.

If you force it open, you won't be able to get in.

A door that opens by itself when you put your heart in it seems like a great thing.

In reality, it's a semi-automatic design that's neither automatic nor manual, requiring a person to cut the rope and control it in addition to the power of the engine.

Because I just watch through the observation window to see whether or not the heart was offered and then manually operate it.

But how would outsiders know that?

"If you are a drone that has transcended your own limitations……."

Among the ten great saints of the Apostles, the saint of the highest order, Junggi-chung, lets out a groan.

Actually, it's not really a mystery.

The ultimate goal was for a warrior to have perfected his own limits.

And when it goes beyond the climax, it's the ultimate climax.

Wouldn't that be a murderous price to pay for the toll, offering the heart of a super-duper unmanned vehicle?
