\chapter{Break through the door and head towards the stars (5)}

It was a rare sight to see three masters of Unrestrained Realm mobilized to dig up a stone wall.

Well, let's say that Jun Gi-chung, who uses a sword, or Povidone, who uses a sword, are like that.

"No, you're going to dig this up with your hands?"

"It's not impossible. It's possible, you rich Zhongyuan guy."

The monstrous monk Amukhaprap, who had no choice but to intervene and scratch the stone wall with his finger,

Of course, Kang-gi's young fingers gently dig into the stone wall.

Although the depth was only about the length of a finger.

Unless you're trying to carve a phrase on the wall, it's not helpful at all.

"Please step back. Don't just take up space. The elder over there was also stepping back."

'Old man over there,' Tian Yuxue shrugs.

Tian Yuxue stepped back, saying that he was not of much help in digging the stone gate since he did not use soldiers.

Then Amukhaprap shouts!

"The oppressors of Zhongyuan always behave like this! They rob and exploit the opportunities of our excellent descendants of the Goryeo Dynasty!"

Suddenly the atmosphere was one of barbarian discrimination.

"No, who even mentioned barbarians? They said they were going to dig a stone gate with the law—"

"We are not barbarians! Don't compare us to the truly uncivilized barbarians like the Nanman, Bukhae, Dongyi, Wae, and Seoyeok! We, the Western Jangjin, are the most spiritually superior people!"

"……?"

It was fortunate that there were no Namman, Bukhae, Dongyi, or Waejeok masters in this place.

Otherwise, it would have been a violent remark that could have led to a showdown between the barbarians, with their pride on the line.

So the two of them split the stone wall and one of them clung to it, struggling.

The Qing party stood back and watched the scene.

At that moment, all eyes in the audience were focused on the stone gate.

It would be nice to run away at this time.

That can't be. Because.

Tian Yuxue asks as if he feels uncomfortable.

-Won't it really get pierced like that?

"Oh, my. I think I overestimated Zhongyuan's organs. I think I was way ahead of my time… "

As soon as Qing's whispering ended, Kuung!

Suddenly, a dull explosion sounds from inside the rocky mountain.

The three masters of Unrestrained Realm stop moving and roll their eyes with anxious expressions.

Tsk tsk, tsk tsk.

With an ominous sound, lightning-like streaks spread across the cliffs surrounding the stone gate from all directions.

Qing saw Tian Yuxue.

Tian Yuxue also saw Qing.

'Let's jump.' 'Let's jump.'

The teacher and student communicate through their eyes.

Then the group looked at each other's pupils, and said, "Okay, two, three. Let's jump!"

The Qing party all turned around and ran away at the same time.

"앗, 저 새끼들! 다여름 저년 짼다!"

Someone points a finger and shouts at the group of Qing people who are walking away in a daze.

Everyone's eyes were on him.

It's a really bad moment, a crack in the cliff right now.

In such a critical time, when one's eyes are focused on a distant place, the moment of carelessness was the most dangerous, as was the case with all victims in the world.

Boom! Boom!

The morning was just beginning to brighten.

Thick dust engulfs the world.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After the dust had been blown away by the wind, only the pile of stones that had been the west gate remained.

The unmanned people, their heads and faces stained gray with dust, stare blankly at the sight.

What on earth was going on…?

Then suddenly, the middle of the pile of stones rattled.

A human hand rises from between them.

"Sir, Your Majesty!"

Suddenly, the Jeolnaksung warriors come to their senses and rush towards the pile of stones.

Taking him as a signal, the ronin and the other warriors looked at each other and then suddenly scattered all at once.

What if the west gate collapses?

You have to go to another door!

The only remaining warriors are the warriors of Gangpaecheon and Jeolnaksung, and some of the Ronin who are friendly with Povidon or wish to move together.

"Your Majesty!"

The exceptionally agile Jeolnakseong warrior, Ilgyewi Daehang Jo Sangchun, holds the raised hand tightly.

And then I pulled it out with all my might.

With a loud crash and the sound of rocks crashing against each other, a person was pulled out.

In that frost, Jo Sang-chun was also thrown backwards.

Two people are entangled as one and slide down the rocky hill.

Meanwhile, Jo Sang-chun checks on Seongjon's safety.

But the person above me was not the saint, but a skinny lama from the western part of the world.

Ah. There was no flesh in my palm.

Two people sharing a passionate gaze within earshot.

Then, the monk Amukharap blushes, turns his head away, and gives an awkward thank you.

"Thank you, thank you."

"Eek."

Why was your face red!

Jo Sang-chun pushed the monster away as if he was starting a fight.

Then, up there, I see the figure of Jeolnaksungjon, who has come out alone.

Now, what a sight the highest peak of Jeolnakseong was clearly illuminated by the rising morning sunlight!

It's so pathetic!

Because from the dusty hair to the hem of his clothes to the tips of his toes, everything was dyed a dull gray.

Meanwhile, only the whites and blacks of the eyes sparkle with luster, and a deep-blue hatred burns.

"I'll kill you……"

"yes?"

"Kwaaaaak! Da Yeoreum! Catch me now! No, I'm going to catch you! That son of a bitch! I'll kill you! What are you all doing lying around! I'm going to beat that bitch up!"

Then he jumps up and runs away, and only then does Jeolnaksung's disciples come to their senses and hurriedly follow him.

The abandoned monster blinked its eyes, then, as if thinking of something, flew after the Jeolnakseong warriors who had disappeared.

"Cheonseungnim? We…"

"We're going too. If we're going to do it, it's better to go through the door with the most obstacles."

Following the fall of Jeolnaksung, chaos will inevitably unfold in the north.

It seems that Gangpaecheon was inferior in terms of military force.

The more confused you are, the greater the opportunity.

And then, only a few ronin remained among the crowd, looking at each other, and some disappeared to the north and some to the south.

Such an empty space.

Povidone's voice echoes.

-Is anyone there? This little brother? Are you okay? Get me out! I'm stuck!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The North Gate appears on the northern foot of Mt. Geobong.

Climbing up the winding observation window carved from crystal, we reach the North Gate opening room, where the Blood Offering technician grins, revealing his rotten front teeth.

"Okay, fight. Fight. Hehehe."

Suddenly, a memory from his childhood comes to the technician's mind.

The corpse of a mother with cloudy, swollen eyes.

My older brother, who was growing cold in my arms.

The Sapa guys who were giggling and saying it was good, and the neighbors who were bowing and collecting coins next to them.

The thought of the government officials beating him up for being so lowly flashed through my mind.

The thick gate of the so-called Jeongpa, which would not open even after three days and three nights of crying and begging.

The world has always been harsh and unreasonable to engineers.

So fight. Kill each other.

Bite each other like the devils of hell.

Just as the world was a living hell to me, you too will have to experience the same suffering.

The Blood Offering technician was excited.

For the past twenty years or so, the arduous labor of digging into the rock has never been difficult for him for even a moment.

The passage I made will become the coffin of those worthless people, and the trap I made will become a spearhead for them to dig into.

So, for the Blood Offering technician, today was the driving force that had kept him living a meaningless life until now.

So fight.

Those who fight like devils and kill each other, and who thus achieve victory, kill each other again and shed blood in the tombs they have dug into the cliffs because of their greed.

I lived until now to see that look on my face.

Blood vessels appear in the eyes of the Blood Offering technician.

Bloodshot eyes await the scheduled bloodbath in front of the North Gate through a small hole.

A sense of tension flows in front of the huge stone gate.

A group of miscellaneous groups led by the three great groups of Sapa, Hyeon-ga-san-cheon, Su-wang-seong, and Gwang-ryong-seong.

Besides that, there are also ronin and others in the group.

The hiking trail to the summit of Geobong was located to the north.

So, the number of ronin and others gathered in front of the North Gate was not inferior to that of the Sapa.

So, it was like they were split in two and were aiming at each other with their weapons drawn.

Standing before Sapa, the holy spirit of Gwangryongseong, Yiryongchang, growls.

"Do I really have to see blood?"

"Even if we open the stone gate, we know you have no intention of letting us in anyway. You want me to sacrifice a single, supremely skilled warrior at a time like this? I'd rather settle things with you here."

"How dare you! Do you dare to oppose the Ten Great Heavenly Saints!"

"Huh. What would we do if we fought against them? We have the land of Sacheon and the land of Shaanxi, so isn't there more than half of Zhongyuan where we can settle down?"

Since it's a sect anyway, isn't it impossible to pursue the political factions' territory?

The eyes of the Sapas, who had already been poked in a sore spot, immediately took on a fierce appearance.

But the man who doesn't care and cynically looks at her was Jong Jeong-pil.

Jongjeongpil, his last name was Jongjeong and his first name was Pil.

He was also a master known to the world as Dokgogeom, one of the best swordsmen in the world.

"Ugh, you're relying on a single, insignificant act of your own to get things done!"

"Do you know? You have a bunch of worthless people over there, and you talk a lot."

"You idiot. You're so dumb. Ilshin was a loner. Even if you're a master, aren't you still just one person? Even if you wanderers band together, you're still wanderers. Do you think you can keep your promise to the end, no matter how many die?"

"Ha. Those Sapa bastards are talking about loyalty. The world really was backwards."

"Ha. Are you saying you'd rather drink the punishment wine than the government's? The disciples—"

It was when King Seongjong of Gwangryongseong, along with the ambassador, was about to give the order to attack.

"for a moment!!!"

A loud shout, filled with all the energy one could muster, cuts through the back of the attack command.

Everyone's heads turn.

A group of drones running fiercely from the other side.

"Stop the violence! I'll open the door! I'm Da-yeoreum! I'm the one who opens all the doors in the world!"

Summer? Does anyone know?

Such glances spread among the martial artists split left and right.

But who knows?

Meanwhile, a taller drone suddenly jumps out from among the running drones, increasing its speed.

The expressions of those with discerning eyes harden.

Well, that speed was incredible.

A study of lightness that can truly rival the world!

"Wait, stop-"

"Get out of the way!"

Even without the stone gate, there are Sapa, Ronin, and others who are divided left and right.

Between them, a ray of light rushes in like a flash.

I see treasure hunters drawing afterimages as if the blue was stretching left and right.

Of course, they are not pushed out, but rather run through the crowd.

Every time the tips of my feet, filled with bets, touch the ground, it feels like the ground was flipping over and exploding with an incredible shock.

Soon, Qing's shoulders fall back.

A clenched fist.

I brushed against his side and sat down behind him, the inside of my wrist facing the sky.

Three steps forward.

The blue shoulder falls back to its limit and disappears completely from the front.

Two steps.

The blue arm swells to at least twice its size.

One step.

A fist that extends at the speed of light.

And then, boom!!!

A huge roar, as if the heavens and the earth were collapsing.

The trees tremble and birds fly up in unison.

The soldiers in front of the North Gate watched the results of that incredible attack with astonished eyes.

A huge pit was dug in the center of the stone gate.

A spiderweb-like crack suddenly appears within a radius of one sheet.

But that's it.

The stone gate still stands firm in its place.

"Friend! Get out of the way!"

A man brushes past the crowd of people.

One man or two black ones.

A clear, bright energy of the sky rises from the swords held in the right and left hands.

As the blue bird jumps up, its long body spins gracefully and flies backward.

And Nan-gong Shencai, digging underneath, stretches both swords straight forward.

Two swords that dig into the handle without a sound.

Two round handles remain in a hole carved into the stone wall.

The flying blue bird touches the ground, flips over, puts its hands on the ground, kicks its legs, and circles back three times.

And then tak.

Bend your knees and place your hands in front of your feet, keeping them close to the ground.

The posture of a person kneeling on one knee.

But from ancient times, it was said that bending the knees was for gaining momentum.

Qing stretches his bent legs with all his might.

One step, two steps, three steps.

The Heavenly Demon breaks the sky with just three treasures. This was the reason why the Heavenly Demon uses the method of shrinking land.

The blue twin fists take up position behind the side.

A fist that narrowly missed Nan-gong Shencai, who was quickly dodging, and then spun forward half a turn.

The Qing's twin fists strike the two sword handles protruding from the stone gate.

Kuung!!

The loud noise echoes again.

Qing stopped with both hands outstretched.

A scene where time seems to have stopped.

Both fists were dug into the stone gate up to the wrists.

The audience swallows their saliva.

A sound that echoes softly in the quiet son-in-law's room as everyone was silent.

Tsk tsk, tsk tsk… … !