\chapter{Break through the door and head towards the stars (6)}

How come people's names are like this?

The two fists of a woman with a very strange name emerge from the stone wall.

When they entered, they were bare-handed, but when they came out, each of them was holding a sword.

Then, the man with the twin swords raised both arms side by side.

The woman twirled her sword in a noisy and stylish manner, then inserted it into the sheaths on either side of the man's waist.

Their eyes crossed as if they were communicating.

The woman waves her palms vigorously, and the young man raises his fists with excitement.

The woman's palm split the air, and the young man's fist also stopped in a shaky position.

The eyes that meet each other again.

Unspoken communication.

Then this time the woman extends her fist.

The man's palm cuts through the air.

People realized.

Those guys, they don't communicate at all.

The two of them looked at each other awkwardly and-

"Miss, this won't do! Let's go!"

"Hmm. Okay."

And then, wouldn't it just fly away?

"Wait! What the-"

Someone belatedly tries to stop him and call him out urgently, but Dahyeoreum's loud voice cuts him off.

"My name was Da-yeoreum! I open all doors in the world! Don't forget to say thank you!"

"Put it in!"

And then, bang.

These are two people who run away and disappear.

The remaining drones blinked, and blinked again.

What the heck? What kind of bastards passed by?

All that remains was a huge pit dug into the stone wall, deep cracks stretching out like spider webs.

Two small holes in the center.

And the liquid keeps leaking out from the two holes in real time.

"Kuaaaah!"

Among the engine technicians, the engine technician of the Blood Offering unit cried out.

"Eww! Damn it! Why! Why are you interfering? Why! Has the heavens abandoned me again!"

The Blood Offering technician was swearing and struggling.

I'm angry and upset, but all I can do was run around and scream in anger, so there's nothing I can do.

But there was something more important than anger to decide.

The Blood Offering technician opened the single-line sound box and reported urgently.

"Your Majesty, Your Majesty was currently at the North Gate…"

Guisanmanbak Amharyong was still in a bad mood.

That was because the plan that had taken twenty years to build kept creaking.

If you feel good at times like these, you may be experiencing dementia or mania.

The decision to blow the introduction was also an impulsive one caused by this discomfort.

Even if there were only three passages left, would he have ordered the demolition of the maze that contained the twenty years of Western pioneering without hesitation?

It was a furious and stern warning.

If you do something foolish, you may not be able to enter at all and may end up buried in the mountains.

Stop using useless tricks and just kill each other quietly to give me the heart of the ultimate master.

The young martial artists who faced the collapsed stone wall of the West Gate will split into the North and South to deliver the tragedy and the stern warning.

If you do something wrong, the entrance will collapse!

I must take out the heart of the supreme master with my sword!

Has it only been this long since he issued such a stern warning?

The North Gate was on the verge of collapse. Should we destroy the passageway now? Or,

"Why!? Why! Why! It's already falling apart! But why! Why! Why! Why was it falling apart again! Are these kids all illiterate!? It's written right there! Heart! Give me your heart!!"

Among the technicians, the leader of the Gonghyeoldan, Guisanmanbak Amharyong, cried out.

-That girl, Da Yeoreum,

"Again! Again! That summer girl again! What grudge does that girl have against us!"

-My lord, the North Gate was on the verge of collapse. What should we do!?

"Ugh, ugh……!"

The dark dragon gritted its teeth.

There are three passages left.

You're knocking down one more here?

Then wouldn't the prepared passage be torn in half?

The dark dragon was not the type to laugh it off and say, "Half of it's left."

"Why on earth! It said we'd open it if we offered just one heart, just one heart! Were we hoping for something big!? Just one heart! It wasn't like we were asking for a hundred people to be killed and sacrificed!"

The dark dragon started to explode with anger.

It was a crimson anger that surged up like lava.

"Just one heart! You said you'd open it up if you saw just that much blood! But you're saying you can't even do that?! We've been preparing for twenty years! These damn bastards can't even give us one heart! How can this be? How can this be!"

The same goes for the North Gate technician who was about to explode with anger.

Perhaps overcome with sadness, the moist voice of the North Gate technician comes through the brass pipe.

-Ugh… …!

Those salty tears touch Amharyong's burning heart.

Thanks to this, Amharyong barely manages to calm down.

"Damn it, the North Gate was open. All personnel, standby for operation in your assigned vessel area. I'll relay this again. As of this moment, the North Gate was open, so all personnel in the Jeongjo are to focus on their mission."

The dark dragon giving orders was bitter.

Offering up the heart of a top-tier expert at the entry stage was not a trick to get a thrill by just seeing a little blood.

It was a task to reveal the true nature of the abominable martial artists before entering the passage.

So, those martial artists who have finally sacrificed the heart of a top-tier master will only then realize their savagery.

I'm talking about the barbarism of those thieving bastards who would even cut down on all the relationships in the world to achieve what they want.

So, once they enter the passage, they can kill each other without hesitation.

In this way, step by step, they are intensifying the slaughter scene where they kill each other like adding fuel to the fire… … .

The cracks that spread out in all directions from the center of the North Gate finally reached the corners, and a faint vibration rose.

"Uh, uh, that thing……!"

The soldiers at the north gate retreated back in a hurry.

And then, woosh!

A violent plume of dust rises with a loud noise.

The sound of the drones coughing loudly was noisy.

And finally the dust settles.

The huge stone gate, one jang high, was nowhere to be found, and beyond the piled up debris, only a gaping, black cavern was left.

"You really, really opened it, right?"

"The door was opened……."

"The one who opens the door, the one who opens the door, the one who opens the door."

If you heard the truth, it would be unfair.

I saw with my own eyes the scene where the door collapsed in pieces when I tried to cut it with a knife at the west gate.

At the North Gate, there will be pursuers following you, so you can't waste time like that.

Since I didn't have much time, I just grabbed it and ran away.

But how could I have known it would actually open?

There was only one thing that Qing overlooked.

As expected, whether it's a person or an object, once you grab it, it will obey you!

That was when.

"Dae-yeoreum-yi! Did you break the door again?"

Jun Ki-chung, the fallen star, falls down with Noh Ho-seong.

And then, as I look around, I am speechless at the sight of a dark, open passageway.

What? It's open?

Junki-chung turns his head quickly, spots a familiar face, and quietly tries to speak to it.

"Listen, Lord Gwangryong, has a year with the ridiculous name of Da Yeoreum appeared here?"

"He appeared. He suddenly appeared, broke through the stone gate, and disappeared. Do you happen to know him?"

"Well, that girl, huh?"

Junki-chung stops talking and looks at the open passage of the Shingajjimyo.

It was because the dark passage suddenly had flashes of light coming on sequentially.

As if to tell us to come in, a torch hanging on the wall starts to burn by itself.

Jun-gi-chung stopped in his tracks.

Come to think of it, what's the big deal about chasing after and taming the summer?

There's an open passage right in front of you, so why bother going out of your way to find that girl and harass her?

A passage leading to the absorption magic was right in front of you.

And then, Sapa's unique rationalization begins.

Why do you chase after Dasummer?

Because she was a con artist who dared to defraud the Holy One of the Great Fall.

But was it really a scam?

If the North Gate had collapsed, I wouldn't know, but seeing it gaping like this, I think Da-yeoreum might really be a master of opening doors.

It must have been those who were cutting the stone gates, not the summer ones, that barbarian lama monk who kept poking them with his finger that must have caused things to go wrong.

What if you didn't trick me?

We need to find an emergency kit as soon as possible.

There's no reason to chase after it and make a fuss, right?

It was Sapa's rationalization of overlooking trivial things for the sake of greater greed.

"That woman headed east all summer. She was a brilliant student of light martial arts. If you want to find her, you'll have to hurry."

The Gwangryongseong Seongjon Lee Yongchang said.

It means that it's done, so get out quickly.

Jun-gi-chung then coughs in vain.

"I'm not really looking for it. Anyway, now that the door's open, I guess I should start exploring…"

At that, Lee Ryong-chang's expression suddenly turned sour.

Why was this kid coming to someone else's entrance and making a fuss?

No matter how you look at it, opening the North Gate was a rational choice.

Since one entrance has already been destroyed, destroying more here would be pointless venting one's anger.

But I can't help but feel a sense of defeat that pierces my heart.

Damn you guys, I have the good intentions to prepare, but I hate giving up my heart so much… …

It was when the dark dragon was swallowing the powder.

-Sir, I am reporting from the alumni association… …

"What, you gave me your heart? Are you going to open it now?"

-That's not it, but it seems like this girl named Da Yeoreum was acting up here… … .

"Again! It's that girl again this summer! Why! Why, even if I open the door, that girl goes all the way there and starts making a fuss!"

-Ugh, that girl named Da Yeoreum was stopped from breaking down the door, and now she's going around saying that she just broke open another door and the fellow students are just standing outside like fools…

The dark dragon roared.

"Just open it! Open it!"

-yes?

"Now that I see it, her goal isn't to open the door! She's just trying to break it down somehow!"

Even the dark dragon was not stupid.

Wasn't she the one who tried to force a hole through the stone gates at the West Gate and North Gate?

When I heard the report from the North Gate, I thought they had come to the North Gate because they had failed at the West Gate.

If he appeared again at the east gate even though the door was open, what would be his purpose?

"So, just open it!"

-Oh, then, Dongmun, I will open it.

"Nammun, Nammun, are you listening? You guys open up too!"

-Yes? Are you talking about now? Here, right now,

"Just open it. At the head of the group. Now, the real bloody battle, the fishing expedition, begins!"

The dark dragon roars solemnly.

Even if you come now and pretend to be a general and shout, it's just a forced operation that went wrong from the beginning.
