\chapter{Break through the door and head towards the stars (3)}

The Jeolnaksung Seongjon Junkichung felt the need to make a decision quickly.

Mount Lao borders the sea to the east and south.

To the northwest was the great city of Jikmok.

Then, naturally, the unmanned troops will flock to the west and north gates.

Even though it's dawn and the sky was turning the color of the sea, it's like this.

I wonder how many moths will fly in when the sun rises.

Where would the troublemakers who rushed to find the magician of absorption go?

You'll probably join a group of ronin or something like that to increase your power.

However, Jeolnakseong and Gangpaecheon had no more people to join.

If I try, it's just a bunch of small and medium-sized businesses?

But aren't most of the anonymous guests who belong to other groups and don't reveal their names just like that?

Even if you stick with Jeolnakseong and Gangpaecheon, you will know that you will be used as expendable goods and thrown away anyway.

Because Jeolnakseong and Gangpaecheon actually had such thoughts.

And if Jeolnakseong and Gangpaecheon had been present at this location, they would have quietly taken off their military uniforms and headed to other forces for the same reason.

In other words, the longer you drag it out, the more disadvantageous it becomes.

"Look, I am the Jeolnakseong Seongjon Jureupdo Jun Gi-chung. As you all know, there was no benefit to stalling, right?"

Povidone nodded to him.

And then, the monsters who were in similar positions as the representatives of other groups also expressed their agreement.

Looking at the power structure, it seems like the Ronin and others would have an advantage if they stalled for time.

but?

There was only one volume of the secret, and in fact, even if there were multiple volumes, there was no intention of sharing the divine power.

So once the door was opened, we were each other's competitors and obstacles.

Just because you're stalling doesn't mean you're good at it.

"What are you going to do? Are you going to take out a heart? Whose heart would you take out?"

"Are you suggesting we draw lots? Even if you were to pluck out your heart and offer it to someone else, who would want to draw lots if you only asked them to do good things?"

Jun-gi-chung suggests a clever idea to him.

"Is it really necessary to tear out the hearts of the martial arts comrades here? Why not just tear out the hearts of those who haven't arrived yet?"

This means that we will attack the next super high-level master together.

Here and there, exclamations of "Ah!" or "Ah…" or "Ah…" burst out.

The expressions of the unmanned soldiers all brighten.

That was when.

"Tsk tsk. You idiots. Are super-skilled warriors really that common? And even if a super-skilled warrior does appear, do you think a master of that caliber will show up alone, without any followers? Then, will the Sado Ten Great Heavenly Saints be in charge of dealing with them?"

A somewhat irritating and cunning voice interrupts, pouring cold water on the situation.

Junki-chung flinched slightly and asked.

"What about you, sir?"

"Tsk tsk, was your head still spinning? If I were going to reveal who I am, would you be standing behind some fake monk like Moknae? You're just an old senior, you punk."

Tian Yuxue said this and lifted Kang Hwan up.

Junki-chung frowns at the tone of speech that's devoid of any sense of courtesy.

But since the amount of work done by old Sapa masters was like that, I was used to it so it wasn't to the point where I felt offended.

"So, your teenage nature was going to come out and tear out your heart?"

"That's not it. The Povidone Master was here, and so was the Monk. If the masters of Unrestrained Realm join forces—"

"What? How can I trust you guys and fight alongside you? If you misstep, you could take out one of our most dangerous rivals. What kind of nonsense was that Sapha kid talking about?"

At that, Povidone and the monster's expressions harden.

When I think about it, it's true.

Even though the teenage nature was a group and could fight back to back, the ronin and the others were merely a collection of individuals who had banded together out of necessity.

"Then, what plan do you have, senior?"

Jun Ki-chung's tone of voice was rude.

But Tian Yuxue just laughs it off.

"Anyway, this was why you stupid kids can't do this. If you were planning on finding Jang Bo-do's treasure in the first place, shouldn't you have brought in a renowned expert on organ transplants? Anyway, you kids who can't even think. Tsk tsk."

"That was a true fact. I agree with you wholeheartedly. The heads of Zhongyuan people are merely ornaments. Their actions in following false Buddhas are proof of this."

The monster nodded in agreement.

Thanks to this, the focus was focused on one place at a time.

This barbarian bastard came here alone, so why was he acting so great?

"Ahem. Are you saying that you brought an expert in organ transplantation?"

"Do you think I'm one of those idiots? Go ahead and open it. I bet you were bragging about how you could open anything."

"Huh. I'm the King of Organs, Dayeoreum. There's no one in the world who's more knowledgeable about organs than me. Those flimsy stone gates? Dayeoreum will open them all."

Everyone in the audience tilted their heads at that.

King of organs?

King was king, John was supreme, God was god, Je was emperor.

Isn't that a crazy and grand nickname that even an emperor wouldn't use?

Is it summer there? What's the person's name?

If you're an expert on such a great institution, you've probably heard of at least one of them.

It seems like no one knows.

"The King of Organs!" "It's summer!" "It's summer!"

At that moment, fortunately, someone pretends to know.

Nan-gong Shencai and Jin Changming were confident.

However, even though I shouted at her, Murong-ju-hee lowered her head and covered her ears as if she couldn't raise her head.

People around me are giving me suspicious looks as if I came with those guys, which makes me even more reluctant to raise my head.

But to anyone who hears it, it sounds like a pseudonym.

If that's not a pseudonym, then you've found your calling and learned it well.

Qing took it a step further.

"Okay. But you have to settle the account, right? You're no ordinary engineer. If I open the door, I should get something in return, right?"

"You bitch. You received the gold ingot and ate it, and now you're talking about money? Have you ever seen such a golden worm?"

"No, sir, you paid your price. If you open the door, shouldn't you at least throw a coin to the little waiter at the inn? With so many people wanting to enter here, shouldn't we show at least a little sincerity?"

It's a call to immediately give money.

It was absurd, but on the other hand, my trust suddenly increased.

Isn't this an attitude that says the door was already open?

Jun-gi-chung opened his mouth to answer him.

At times like these, it was natural to gain authority by striking first.

If this continues, you will be secretly treated as a representative or host.

"Hey, you really can open the stone gate?"

"I'm Da-yeoreum, aren't I? Don't you know Da-yeoreum, the brilliant sun of the Organism-Cultivating World? By the way, who are you, sir? Are you famous? I don't know anything about martial arts."

"what."

"Go! This person was the Holy One of the Great Falling Star! This young woman was truly reckless!"

"Huh. Is the Pojeongsa Temple any better? Hmm? By the way, Jeolnakseong? Is there another city in Zhongyuan?"

"This ignorant bitch!"

"stop."

Jun Ki-chung stops the disciple.

After hearing what he said, it seems like it's not a pseudonym but his real name.

A martial artist knows how the martial arts world works.

What on earth was the organ diagnostic system?

I've never heard of such a thing.

So, even if he was a famous organ craftsman, it would be unfamiliar to a martial artist.

So even a craftsman may not know the martial arts world.

If she doesn't even know the name of the Apostles' Ten Great Natures, then isn't she just a bitch who stays shut up and touches the organs?

"Okay, how much do you want?"

"Hehe. How far did you see?"

Jun-gi-chung was speechless at that.

What the heck was this?

Doesn't the seller set the price of the item?

How far have you been watching?

Is there a price to open the door?

No, that's just like the saying goes, only those guys who call themselves organ dealers know the market price. How would someone who asks you to open the door know the market price?

This was truly overwhelmingly unreasonable!

Junki-chung felt anger boiling up deep in his chest.

"But how many people are there? Oh my, when are you going to calculate all this? Pojeongsa Nari? You're going to do it all and just give me one gold coin?"

Junki-chung was angry and speechless.

"You want me to pay for all the people here? Me? Why?"

"Of course, the Pojeongsa Nari was the highest ranking person. If you pay the price to open the door, wouldn't it be more beneficial for you as well?"

Jun-gi-chung, who was about to get angry after hearing the answer, stopped.

Convincing… …?

Why would we pay the price of opening the door to those who are competitors and obstacles anyway?

It's literally like throwing money into the gutter.

But that's not all!

It was a matter of buying a cause more valuable than the price of opening the door.

Since I paid for you to open the door with my own money, it's a justification and authority to control the order of entry and even whether you can enter or leave.

"What a clever woman. Good."

"Wait a minute! We'll pay the price—"

Povidone, who had been listening to the conversation, quickly intervened, but Jun Ki-chung was quicker.

"Wow! The gold coin just popped out! Thank you!"

"Here you go, young lady! We'll pay for it ourselves, so give us change for the number of heads, quickly!"

"No, I received the gold ingot, but where's the change? Don't do that. Give it to the Pojeongsa Nari here!"

"That damned swindler's lament! That guy, no, that person isn't a swindler!"

"You are the supreme ruler of Jeolnakseong, but you are not a commander? Huh? Are you Commander Nari?"

"No, there was no such thing as Jeolnakseong!"

"Oh? Then what was Jeolnaksung?"

"It's not a surname, it's a martial arts school!"

"Wow. Now even martial arts schools receive titles? I should have read the secrets instead of studying the organs."

"Ah! It's so frustrating! Why can't you understand me?"

Povidone pounded my chest.

Ripples form in concentric circles on the obese flesh.

Qing looks at the sight with wonder.

I think it's bigger than me?

Why can't we just give the title of Samdu to that pig?

Anyway, Qing was moving towards the organ.

Everyone obediently gives way, as if they naturally believe that the King of Creatures will open the stone gate.

Tian Yuxue was pleased.

Isn't it a natural fraud like flowing water!

He asked for money so confidently that he really looked like a master of the institution.

It was a skill that boldly skips the time to check whether the skill was really good or not, and even earns gold.

Of course, it's because the disciple didn't study.

Isn't your head not good?

It was something that the vast majority of parents believed in as if it were their religion.

But, the brain was originally divided into a head for studying, a head for work, a head for the rest, and a head for growing hair.

So, we must keep in mind that if we are overconfident in the heads of our children, disciples, etc. with wrong beliefs, it can result in misfortune for both you and us.

So, Qing stood in front of the stone gate.

The group stands guard in front of the stone gate, pretending to escort the agency's expert, Da-yeoreum.

"Come on, let's see. What a great organ system this is, oh. oh."

Qing-i was bustling back and forth, knocking on the stone gate and putting her ear up to it, pretending to listen.

Then put your hand into the hole where your heart was inserted.

After gently sweeping, he presses firmly, clearly showing the tendons on his forearm.

Other people can't tell by looking at it.

It means that the tendons on the blue arm are sticking out.

A truly transcendent force was pressing down on the inside, left, right, and above the heart hole!

And Qing was inwardly confused.

Hmm. Why doesn't it collapse?

Since this was the linchpin, I thought it would collapse if I touched it roughly with force?