\chapter{Break through the door and head towards the stars (9)}

Qing looks at An Yun-juk blankly.

An Yun-juk rolls his eyes as if he was anxious.

She was a woman who immediately caught a person.

It wouldn't be strange if he suddenly swung his sword.

As expected, Qing pulled out his sword with a serious expression.

For a moment, An Yun-juk's head spun wildly.

Should I pretend to be crazy and just go for it?

But the grip that was holding my hair was as firm as steel, so even if I didn't know about my internal energy, I was sure that I was a master of formidable external energy.

An Yun-juk was not a master of internal energy, nor of external energy.

Plus, it's the old days.

Even if you exclude the famous Joayo and the even more famous slaves, it's five to one.

It was as hopeless as an ant fighting a man.

But I can't just give up my neck.

Countless scenarios popped into Ahn Yun-juk's head and disappeared hundreds and thousands of times.

An Yun-juk, who has finally discovered a possibility, makes a desperate resolution.

And just as Qing was about to open her mouth!

An Yun-juk threw all his strength into flying.

Towards the floor!

"Oh my! I, An Yun-juk, am not a ignorant man. My martial arts skills may be humble, but if you ask me to cook, do laundry, make the bed, and keep the guest room, I will do everything as a servant."

He thought of Qing.

what?

"Okay, get out of the way."

"yes?"

"Vicky, please. Look at the door."

It was Qing who was looking at the automatic doors that actually existed in Zhongyuan.

What kind of guy was acting up in front of me and then suddenly bowed down and told me to treat him like a dog or a horse?

"Ah. You were looking at the door…"

An Yun-juk stepped back with an expression on his face, as if he was about to die, and clung to the wall.

Qing approached the stone gate and examined it in detail.

Isn't it just an ordinary stone gate?

What on earth was the principle behind this thing going up and down?

It seems that the stone gate came down through a pre-dug groove and took its place.

It's an incredible fact that's hard to believe, but the absolute king of the organ-generating world, Da Yeoreum, was actually a fraudulent liar.

In the summer, I only know the basics of organ transplant.

The reason I know G was because anyone from the Qing hometown can see and understand the basic operating principles of a machine.

It's not a question of intelligence, it's a question of familiarity.

What kind of complex device could there be in such a single stone gate?

Even if it's just a pulley or something that opens up and down, it's still a great new technology at Zhongyuan level.

But according to the Master, the last demon who was the owner of the Shingamyo, Shin, had been dead for over a hundred years.

Frankly, even in Qing's hometown, it's already an obsolete piece of junk that doesn't work after a hundred years.

But in this uncivilized Zhongyuan?

Qing slowly extended his sword.

Through the blood vessels that stretch out like an eight-lane road, the strongest energy pours out.

Even without that, the thick Moonlight Sword (10th size) has a blade that's only an inch thick, and it's filled with ignorant swordsmanship.

It becomes a vicious sight, as if the sword was doubled in size from left to right.

The tip of the vicious weapon begins to silently dig into the stone gate.

Slowly. Slowly… … .

Qing focuses all her attention on the sensation of her fingertips.

Even while cutting the entrails of a flabby person, he was a person who understands the taste of cutting the muscles, tendons, bones, small intestines, large intestines, liver, lungs, kidneys, etc.

What about the feeling of poking a stone?

What the heck? It's all just stones?

Then, the tip of the sword suddenly becomes loose.

The stone ended and met the void.

Qing immediately put away his sword and put his face into the hole I had made.

Across the dark passage, there was a tiny hole, like a needle hole.

A faint light shines through the hole.

What was it? Is it across the street?

I guess I can just break through.

Qing's mind was at ease.

Now that the escape route has been secured, it's okay to run wild inside.

If anyone knew, they might wonder why this girl was suddenly so smart, or if she ate something wrong.

But Qing was originally a petty person who takes his own safety very seriously.

She was always a selfish girl who would always find a way to escape even if it seemed reckless!

However, as I was disguising myself and pretending to be someone else, I seemed to have become absorbed in it without realizing it.

It seems like they were talking too much without any context, saying that the character would disappear anyway, whether it was Yun Yuanying or Da Yeoreum.

It's not that Qing was stupid.

Because this was human instinct and nature.

Anonymous!

When a person was anonymous, he has nothing to fear, nothing in the world he cannot accomplish, and he becomes the most authoritative scholar in every field and the greatest genius of the century.

Then, a stone gate came down behind him.

It was a moment when the path of retreat was blocked.

Then, the survival instinct that had caused me to leave home due to anonymous threats returned.

A rapid rise in intelligence in the face of crisis!

She's such a cockroach bitch.

Of course, there was no scientific basis for the idea that cockroaches become more intelligent in the face of crisis.

In that sense, you could say that Qing was worse than a cockroach.

Qing turned around.

The Qing's behavior pattern was always based on escape.

In other words, if it doesn't work, then it's irresponsible to do something like that.

And now if it doesn't work, you can just throw it away.

Doju was a god and Qing was invincible.

"Mr. An. Should I call you Mr. An from now on? No, isn't it a bit awkward to use formal language with a servant? Right?"

"Yes? Yes, that's right, but……."

"What was it? Your expression seems a bit sour."

Well, it was An Yun-juk who declared himself a servant because his feet were numb for no reason.

But as the saying goes, a man's words are worth more than a thousand pieces of gold.

Through this, we can see that a woman's words are of little value to Zhongyuan people.

This was why it's okay to talk nonsense as soon as it comes out of your mouth.

"What? Haven't you seen someone drive a sword into a stone wall? Is Mr. An's body stronger than stone? Then, instead of a servant, do you want a scabbard? Let's see, where should I put the lead sword?"

The role of the scabbard was to hold the sword.

Of course, a human servant was a much better choice than a human scabbard.

"No! It's an honor to have you as your guest!"

"yes?"

"yep!"

"Yeah. It's nice to have a loud voice. Let's do our best."

"Yep! I'll do my best!"

What do you want me to do well, and what do you intend to do well?

I didn't know Qingdo or An Yun-juk.

But I guess I have a rough idea, so whatever.

"Okay, I told you to fill the table with ten people. There must be a reason I told you to fill the table with ten people. Let's start with our names. I'll just leave."

At that, Lee Hye-hye's expression became blank.

Why are you leaving? Why are you leaving?

"And the old man here was a thief."

Tian Yuxue avoided his gaze.

Joayo's thoughts stopped for a moment.

A thief?

Let's say he's a thief.

Why are you telling me that?

Although Lee Hye-hye was confused, Qing continued speaking without paying attention.

"This little, tiny kid here was my younger brother Makjageum."

Chen Changming's expression became fierce.

A tiny little brat, in short, it means very small and tiny.

Wasn't Chen Changming worried about his already unstable height?

"This was Muyang Sojeong, and this was Geomijang, my swordsman friend."

At that, the corners of Murong Juhee's eyes drooped.

Elder, younger brother, swordsman friend.

But here? Here?

While Murong Juhee was feeling discouraged, Li Huihui finally understood Qing's words and actions.

I wondered what it was, and it was a public announcement!

"Well, if you're going to use a pseudonym, wouldn't it be better to be a little more sincere?"

It's a confident pseudonym that anyone can recognize.

Now, it's just a case of people making up pseudonyms.

Qing was confident.

"Oh, a pseudonym? You're not playing around with people's names. I like this name. No, I like it."

At that, Lee Hye-hye furrows her brow.

"Joayo was not a name, it's a nickname."

"That's why I was joking around with nicknames."

The escape route must have been secured. Qing smiled and became intoxicated with anonymity again.

It means talking nonsense.

"What the heck, no, haa…. It's okay. We're in the same boat anyway, just like you said. You know me, right? I'm Joa, Lee Hye-hye."

It was a martial art that uses a huge iron claw, so it uses claws and fangs to claw.

And the word ‘Yo' (妖) means witch and was usually used to refer to a young female horse.

A witch? What's so magical about it?

"This was Ilno, Ino, Samno."

The eyes of the group narrow at him.

How come people's names are slave number one, slave number two, slave number three?

As the group blinked, Joayo raised her eyebrows in annoyance.

"I didn't do it. Those filthy bastards did it themselves."

"That's right. Serving you was my sole destiny. Since meeting you, I have decided to live as a mere slave, so I have abandoned my name."

"Hmm." "Right."

The two remaining men nodded in agreement at Ilno's words.

Qing looked at Joayo again.

What was it? A devilish woman?

The sharp eyes and fierce mouth make him look fierce and dirty.

"Ahem, my name was An Yun-juk-"

Pak! Qing hits the back of An Yun-juk's head as he was about to introduce himself.

"Hey, Mr. An. What are you weighing now? This was my servant, Mr. An, who I picked up earlier."

Qing stroked An Yun-juk's head.

The back of its head was unusually flat, so it seems like it sleeps straight and looks like it's dead.

"……This was Miss Mak's servant, Mr. An."

"What? You're a little slow to respond? And what's wrong with you, Miss? I'm not that kind of precious woman."

The noble lady, not the Qing (the emperor's daughter), said.

"Oh, then, ma'am?"

"Madam, what? You look so old?"

"Then what should I call you…?"

"Just call me 'Master' comfortably. You said you'd do anything for me, right? I'll treat you as comfortably as a dog."

I'd rather have a young lady or a madam.

If you are the master, aren't you a slave rather than a servant?

But An Yun-juk comes to his senses.

You've fallen for a really bad bitch!

If I do this wrong, it'll really become a scabbard!

"Yes, hehe, master, treat me like a dog. Hehe."

"Okay. Let's do our best."

"Yep! I'll do my best!"

I don't know what he's so good at, but Ahn Yun-juk's answer was very fitting.

"Excuse me, Master? But, that young lady was staring at me intently. I wonder if I've done something terribly rude."

Qing looked back at Lady Murong.

Eyes full of emotion look at Qing.

Like a large dog wanting a treat.

Qing hit the back of An Yun-juk's head.

"Don't be ridiculous. Who's looking at you?"

"Ugh……"

An Yun-juk was wronged.

I said the right thing, and it was right, so it's unfair.

It was also because of Murong Juhee who glared at Qing with eyes like axe blades as soon as he turned around.

But Qing doesn't really care about An Yun-juk's grievances.

What was the reason for bringing Anyunjuk in the first place?

Even a simpleton's evil deeds are high.

I just chose one item that I wouldn't regret throwing away if I had to.

"Okay, Mr. An. Let's go!"

"Oh, you mean me?"

"Can't you just listen when I'm speaking nicely? Don't you understand the situation? If you're going to be stubborn, you can just go alone. Then I'll have no choice but to send you first. But if you're going to lead anyway, it's better to have a reliable companion."

Even if you get kicked out of the group, it's still the same as being pushed to the front.

At that moment, Mr. An's eyes darkened.

Are you saying that you are leading the way knowing there will be some kind of trap?

I just feel like I got screwed by a crazy woman for no reason.

So, An-ssi took the lead, and Jo-a-yo and the other slaves took their places at the back.

A passageway with a subtle curve.

Qing realized why he had sighed at the annoying structure of Tian Yuxue.

There are some that are subtly bent and cannot be seen in which direction, but there was absolutely no way to see what was on the other side of the passage.

So what about Mr. Ahn, who was in the lead?

I feel like a trap was popping up somewhere right now, and my feet are slow to take each step.

Qing hit the back of An's head.

It's flat, so it's a good angle for hitting.

"Miss, go fast. What good was a man with such small courage?"

"There might be something like a trap……."

"Ah. A trap. Right. Sir, please give me some rope. Our servant could be in danger."

Qing ties a rope around Anyunjuk's neck.

"Okay, done. Now, let's go with peace of mind!"

"Um… what was this?"

"It's a lifeline. If a trap was triggered, I'll pull it and rescue you. That way, no matter what trap appears, you'll be safe, right?"

An Yun-juk, who suddenly found himself on a lifeline (leash), desperately controlled his expression.

If a trap really appeared and you pulled it, wouldn't it be the case that your cervical vertebrae would come out first?

Are you blatantly trying to kill me?

"Uh, Master? Would it be alright if I put a towel over here?"

"Oh. That's a good idea. Hey, Mr. An. I didn't see it that way. You're smart, aren't you?"

"Heh. Hehe……"

An Yun-juk broke out in a cold sweat.

It's not that I'm trying to kill you, but rather that I don't care what happens.

And it wasn't just Qing's attitude that made An Yun-juk feel cold.

"Excuse me, I really don't know, but Miss Muyang? Did I do something wrong to her? If I've been rude in any way, I apologize, so please don't be so arrogant…"

"Huh?"

Qing looked back.

Qing-i, who met the eyes of the smiling Murong-ju-hee, hit the back of An Yun-juk's head.

"What? Mr. An, are you already seeing things?"

"Ugh……!"

An Yun-juk was truly wronged.
