\chapter{Break through the door and head towards the stars (11)}

Qing's gaze scans the room.

Two, four, six, eight… … .

There were forty-two people in total, all of whom were broken, punctured, and incomplete, as if they had been trapped.

Qing looks at the numbers on the stone gate again.

Twenty one.

Forty-two, twenty-one. Isn't that exactly half?

Is there some kind of incomprehensible, cutting-edge, mysterious internal energy organ in Zhongyuan that detects the number of people and reduces them by half?

Then suddenly he tilted his head.

No, let's set aside the number of people. Then what was the writing on the stone gate?

Since there are five passages, the maximum was fifty people, so half of them are twenty-five, and roughly speaking, the minimum was twenty people. After detecting the number of people, the correct number comes down?

But it doesn't seem like everyone cares.

I can't understand Qing at all.

In fact, it can be said that Qing's attitude was very bad.

It was the perspective of a so-called enlightened person who thought, "There's no way Zhongyuan could have such advanced technology!"

His homeland was a world that's far superior to and absolutely advanced in technology compared to the primitive people of Zhongyuan.

So, the attitude was that an advanced civilization that could only come from one's hometown could never come from primitive people.

This was the perspective of so-called civilized people on an uncivilized society, and it was also a secondary cause of numerous massacres and exploitation.

(For reference, the root cause was greed)

Let's say monkeys invented a mechanical clock.

It's amazing, but from the viewer's perspective, it's impossible not to think that there's something ridiculous about it.

On the other hand, from the monkeys' point of view, it may be surprising, but they would not necessarily doubt that it's impossible.

So, the answer of the primitive man who was famous for being the most intelligent among the primitive people of Zhongyuan was this.

"How can you pinpoint exactly half the number of people and tell them to kill them? It's not like anyone's watching."

"Huh. Does that make sense? A hundred-year-old tomb would be haunted by ghosts. It's just a coincidence, isn't it? Perhaps in the next passage, they'll tell you to split into groups of seven, like they did at the entrance?"

"Oh, I see……."

"How do you know how many people will fall into that trap in the first place?"

"But what if we all get swept up in the trap and twenty people come in like this?"

"Huh. Was that really such a serious trap? A nimble guy would have avoided it long ago."

"Hmm. Is that so?"

Now that I hear it, it sounds very plausible.

Qing's doubts were put aside.

Well, it's a world where people breathe while muttering to themselves, and they take in the energy of the world, fly, jump, emit light, and shoot rays.

Even the organ transplant won't go back to the original state.

Well, first of all, forty-two has to become twenty-one.

And then suddenly, a certain emotion wells up.

Qing's killing of the wicked was initially a matter of survival, and after becoming a master, it became a matter of compromise.

But what about cutting down those people blinded by greed right here and now?

Isn't this just a tragedy of people killing each other, playing into the hands of a wicked man who died a long time ago?

Just to get through the stone gate, to get the magic, I have to kill half of this place?

That's, um.

Wow! Infinite supply of villains! Infinite filling!

Unlimited killing! (number limit)

The deceased sucker was the best!

Why are there only red guys gathered here?

The corners of Qing's lips form a pretty curve.

Should I just cut them in order of highest bad karma?

Anyway, if we don't kill the injured ones now, they'll die on their own, so we just need to keep them alive and fill the headcount.

Qing was like a child in an all-you-can-eat restaurant, trying to decide what to kill first.

In the cave, a disturbing atmosphere begins to appear.

Anyway, only twenty-one people need to survive?

Of course, it's advantageous to fight together.

People who have met each other in person or know each other somehow exchange glances and communicate with each other, slowly narrowing the distance between them.

That was when.

"Look! If we're going to cut it in half anyway, wouldn't it be better to have some fun while we're at it?"

One of them suddenly screams.

He was a handsome man with an unusually white face.

But apart from the handsome face, how can we enjoy it when we are about to kill each other?

Even though you and I are not normal people, isn't that too much of a stretch?

People give him cold stares, but the man just smiles brightly.

"I am a man named Damhwajong. All the women of the world call me the Four-Way Master, for I am well-versed in the Four Arts."

Okmyeon was a nickname given to a handsome person.

Qing-i's little brother was worth the nickname. Someone came to Zhongyuan and became the most beautiful person in the world, which was not even in his fortune. I was raising my priority.

"Saryuumma!" "Saryuumjeok!"

As expected, the old traditional etiquette of Zhongyuan comes out.

Qing nodded to him.

Ah. You're a pervert son. You're a castrated son.

The expressions of those who saw the man were rotten.

In fact, Madu, a famous pervert, was treated as a dirty bastard even among the other Madu.

According to Qing's observations of the various evildoers of Zhongyuan, there was no difference between a lustful demon and a devil.

Why, there were only a few people who died after being teased by the Qing.

I can't even remember clearly whether there was a guy among them who was known as a pervert.

In fact, Qing's observation was correct.

The Madou men consider forcibly taking women to be a proud act that they can boast about to the neighborhood.

But there was also a difference between a sex demon and a madou.

The devil tries to rape people when his blood rushes down from doing bad things, but the pervert has been wandering around for that purpose from the beginning.

Either you have mastered a martial art of the Chaeum series, or you have been determined to force yourself to do it from the beginning.

So, from the perspective of the madhus, if they were treated in the same way, it would be so unpleasant that they would immediately decide whether to fight or not.

사람을 잘 죽이면 호쾌한 영웅이지만, 여인만 쫓아다니면 발정 난 개새끼 아니냐고.

In any case, for that reason, the people gathered in the cave roughly understood what the sermon was about to say without even hearing it.

As expected.

"It's already lonely with all these dark-skinned men around, so wouldn't it be better to bring in some women?"

The gaze of the audience spreads to the group carrying the female warrior.

The group that had been stared at moved cautiously towards the Qing group with anxious eyes.

Naturally, the group splits into the group of men accompanied by women.

Qing thought it turned out well.

It's already ambiguous as to who to kill and who to spare.

But even in this situation, wouldn't the idiots who can't come to their senses and follow the orders of the dicks come together on their own?

But Qing's eyebrows twitch.

Isn't this a bit hurtful?

How dare you open your mouth in front of me?

Who are you inciting in front of?

Qing suddenly stands up and draws his sword.

"You guys are saying things that are too much to even dare to say, so I can't just sit there and take it."

"You can take it sitting down, but you have to take it lying down!"

But suddenly, someone started shouting and the bell rang out in laughter.

But the laughter that was not limited to time and place soon stopped.

Because the blue was spewing out strong energy.

"The girl won't be easy either, but you are many and we are few, and we have people to protect, so we must find a strong elder to fight alongside us."

People look at him and wonder what he was talking about.

"Who was the strongest elder among you? If you could come to us, we'd probably be able to balance the scales."

Then, a voice answered among them.

"You seem to have some talent, but that's a bit presumptuous. Why would you insist on being on the weaker side?"

He was a middle-aged man with gray hair at the base of his ears.

This was the main characteristic of the phenomenon commonly called the "banbakguijin", where when the hair grows old, the wrinkles smooth out and the hair turns black again.

It was not a complete reversal of nature like a half-life cycle, but it's a state of regaining youth to a certain extent, and this was called a half-life cycle.

"After all, there will only be one owner of the divine power. Why should we share such a precious thing? Then, if a fight arises later, it will be easier for you, Your Majesty, to side with the weaker ones, right?"

"Huh. They're all the same. And even if a woman who spits out energy says something like that, what difference would it make if we just cut down your men and dragged away the women in equal numbers? Or, wouldn't there have to be some other advantage?"

The master of Unrestrained Realm smiled wickedly.

Anyway, old or young.

Qing hesitated for a moment, pretending to be speechless, but then nodded with a solemn expression.

"Please do as you wish, sir."

"Hmm. Right. She's quite the woman."

And then he leads his men and walks briskly towards this side.

"Wait, Taesanmagun! Please listen to me for a moment!"

It was a conversation bell that shouted urgently.

Qing's ears perked up.

Taesanmagun? The name alone was cool.

I thought, "He must be a very famous person."

Well, it would be stranger if the master of Unrestrained Realm wasn't famous.

"That, isn't that some suspicious woman whose name we don't even know, despite being a female master of the highest order? But we know the weight of your name and respect you, so we'd like to serve you!"

"Hmm. Is that so? You, woman, what's your name?"

"I heard it was a final exit, but since I was an unknown guest, I don't think you would have heard of it-"

"Look! Isn't that a very obvious hiding of identity!?"

Taesanmagun stops in his tracks.

Unlike the realm, the ears are thin.

"And, wouldn't the result be the same anyway? If I just take women, as you said—"

"stop."

Taesanmagun took the weight.

And then he quickly advances towards the group of Qing and his men.

"Uh, why……?"

"One. Are you telling me to swarm you and eat you like an animal?"

The expression "Hle" refers to the mating of animals.

"Two. Would I be comfortable with that pervert?"

It was Taesanma-gun who hated perverts and came with sinister tricks.

Could this be called xenophobia?

Anyway, with the Taesan Demon Army joining in, the numbers were roughly even, and the men seemed to be more intimidated.

He Qing approached Taesanmagun, bowed respectfully and bowed.

"Thank you, sir. The girl will bow."

"Yes, you're a well-mannered child. It seems you've learned proper etiquette, haven't you?"

It was when Taesanmagun was smiling happily.

There was one thing you should know.

When Qing kneels, he must carefully examine whether there are any adults around him who truly follow this vicious murderer.

And if there are no adults around, you should be very tense and not let your guard down.

Because the knees of the blue are usually bent for propulsion.

What if you don't know this common sense?

It has to be done.

The young man bows deeply and suddenly stands up, extending his sword.

The blade, extended without any warning or life, shot between Taesan Demon Army's legs!

It was said that in the past, Qing had a heart attack while wearing a protective mask.

Because the cervical spine protects the bones and muscles.

It was not a universal protective shield that surrounds the skin and blocks physical impact.

The woman's breasts, covered in fat, were out of the protective range.

It's not just that women have a big weakness, but men also have a weak spot that's unprotected, located between their legs.

"Ugh."

A soft scream.

But the greater the pain, the less the screams.

No matter how skilled a person is, a man was still a man.

Taesanmagun grabs my leg and my back bends like a bow.

Of course, not back, but forward.

Because it's a weird moment when you bend backwards.

Qing, who had just let go of his sword, grabs Taesanmagun's head.

And then boom!

A power beyond human reach turns the neck.

If only he had been beaten or stabbed with a sword, how could he have protected his neck as it turned in the excruciating pain of his heart pouring out?

Taesan Demon Army's vision spun around.

The feat of looking at the ceiling while bending over!

After spinning it around two more times, just in case, Qing rips off the head.

If you are a master of Unrestrained Realm, you might be able to survive even if your neck was twisted.

dump.

The body of Taesan Demon King, who lost his head, sag.

Qing raised his head and shouted.

"Enemy leader! Defeated!"