\chapter{Break through the door and head towards the stars (10)}

The lifeline that Qing created was not aesthetically pleasing at all.

Well, wouldn't that be putting a noose around someone's neck and holding the leash?

This was especially true for the people of Zhongyuan, perhaps due to some unconscious fear inherited from their ancestors.

Because all the middle class people are descendants of slaves, second-class citizens, who were strung up in a line by madmen on horseback.

This was before the Zhou clan, who did not want to be a slave, rose up and took the throne on their own initiative.

So, no matter how much slaves were persecuted in Zhongyuan, it was rare for them to be put on leashes.

If you try, it's only used when the police are transporting criminals.

But there were those who focused on the lifeline's ugly appearance.

Lee Hye-hye's three loyal slaves shoot sparkling glances that don't match her large body.

At that, Lee Hye-hye sighed deeply.

"I can't. No, I won't. If you keep going like that, you're a total idiot. The rumors are already bad, so what will happen to me?"

The slaves bow their heads in despair.

It feels a little uncomfortable to hear that.

What? Are you arguing now?

That was when.

"Ugh."

An Yun-juk actively falls on his buttocks, making a sound that makes his breath stop.

It was a violent collision that made me worry about the safety of my tailbone.

Why did An Yun-juk, who was doing fine, fall?

Well, that's because a terrifying force pulled the leash.

A force so strong it could hit the cervical vertebrae, squeezing the windpipe and pulling it in.

Even a skilled player wouldn't be able to do anything about it.

Even An Yun-juk, who was not even a skilled player, had no choice but to roll on the floor due to the strong impact on his tailbone.

Tta-tta-tta!

At the same time, sparks flew from the stone wall.

A fiercely fired arrow narrowly misses An Yun-juk and hits the innocent wall.

"Huh, huff, huff."

A drop of blood gushed out from the tip of his nose where the arrow had grazed him.

An Yun-juk, who had come back from the dead, looked at the small marks on the wall where the arrow had struck, and touched his sore neck.

The rough texture of thick rope.

It was a real lifeline… … .

An Yun-juk breathes a sigh of relief.

For some reason, the tight collar around my neck feels a lot more comfortable.

"Wow, a trap!"

Qing's eyes lit up.

Is there really a trap?

Isn't that pretty serious?

Qing looks at the wall from which the arrow flew.

I can't see the arrow hole?

But I feel like I can vaguely see the outline with my superhuman eyesight, so I try to feel it.

A hole was hidden within the pitch-black shadows of the rough stone wall, sharply shaded by the blazing torches.

Wow, this was really bad.

So a simple major change.

The group that had been following us vertically now spread out horizontally.

On the left and right are Tian Yuxue and Nan-gong Shin-jae, while Chen Changming and Murong Ju-hee are on the inside.

There are two groups of slaves standing on the left, right, and back, and Lee Hye-hye standing in the middle.

As we continued on like that, bang!

An Yun-juk's new model was coming down!

The leash snaps! Dangle, dangle. Dangle.

"Ugh! Creak……."

An Yun-juk's breathing suddenly stops.

As I desperately try to hold on to the lifeline that's strangling my neck, at some point my body starts to float up with a pain that feels like my scalp was being ripped off.

"Ugh, ugh! Keu."

An Yun-juk lets out a rough breath.

Either way.

He approaches the hollowed-out floor and looks down.

Deep down, rusted iron bars held their spearheads pointed skyward.

"Huh."

Before we knew it, An Yun-juk, who had been crawling, poked his head out, then backed away in a hurry, feeling embarrassed.

From then on, whenever he gets bored, the trap will activate and attack An Yun-juk.

Even a perfectly smooth rock falls from the ceiling with a thud!

A giant axe blade cuts through the air.

Chewing hot boiling oil was pouring down.

Blades of spears also sprouted from the floor.

Each type was different, so it seemed as if they were foreshadowing that there might be traps like this in the future.

After Anyunjuk, who was not particularly pitiful, saves his life about eight times, the long passage finally ends and a large stone cave comes into view.

The cave had four open passages without decoration, five if you include the passages through which the Qing entered.

And on the other side there was a closed door.

Above it, several lamps shone brightly, as if to show the inscription on the signboard.

"rest"

It meant to rest.

Qing was speechless. So are his party.

Why are you even giving me a break?

"What should I do? Should I try to break through it?"

"Arthur. It's not too late to decide after seeing how things go. But this—"

Tian Yuxue frowns and moves his mouth.

"You. Even if you're disguised, aren't you being too reckless? Hiding your face and name won't evade the swords and traps. Can't you calm down and act calmly?

"Huh? What was it?"

-You came here to play? Even if you and I both have no problem getting along, what about that kid who followed you? Why are you acting so thoughtless?

"oh."

I suddenly felt like I had been splashed with cold water.

Honestly, I'm a little excited.

The mask worn over the face was so stuffy that it reveals its presence at every moment.

It was like the realization that I was hiding my identity at every moment, so I got excited without realizing it.

In fact, it's more of a side effect of being a disguised person than being stupid and careless.

You can understand this by participating in preliminary military training in the Qing's hometown.

Even people who are usually careful not to get their clothes dirty and immediately wash off any spills of drink with water, will end up lying on the dirt floor after putting on their military uniform.

The normal self and the self as a reserve soldier are different people!

That's why, whenever they have time, they sit, lie down, chatter, and make excuses, whether it's dirt, grass, or stone.

By the same principle, this was also the reason why the men who participated in the preliminary military training made baseless claims that they were experts in their respective fields, rich people, or challenger-level masters of the virtual world.

What? Was the reserve a gathering of successful people?

Qing, who had been recalling memories of her hometown for a long time, reflected on her actions.

Then he looked down at the leash in his hand.

"Hmm. Mr. An, I don't think the leash was quite right. You can take it off now."

"Oh, no!"

"Hey, I guess I was a bit harsh. I'm not just saying this in vain, so you can let it go now."

An Yun-juk walked at the very front of the group.

And then came the pouring traps.

As I looked back on the cause of my regret for falling for that crazy woman, I realized that I had stepped into a dangerous situation that was not suitable for me in the first place.

What kind of magic absorption technique was this, for someone like me, a second-rate person who barely handles true energy and has just started studying?

In the first place, don't fall for the tricks of your sworn brothers and live quietly in Geonyang.

What? I'll fight bloodily to get the magic, so if I hang around, I'll have a chance to steal it?

If you think about it calmly, it was just nonsense, but was I blinded by the words that it was a martial art that would make me the best in the world?

And what saves a worthless life in this brutal wilderness?

Lifeline! It's a lifeline!

An Yun-juk uploaded the napjuk.

"No! Please, Master, your grace was like the sun and the sea. Please, do not take away this lifeline you have given me. Please…"

"No, I didn't mean to beg that much……"

Qing looked back with a sour expression.

Tian Yuxue sighed deeply, and Chen Changming shook his head.

No, what was it?

Anyway, since I was told to rest, I decided to rest for now.

I had a slight urge to break down the closed stone gate right away, even though it was just a break, but there was no reason to ignore the written words and go that far.

That is, I want to cause a ruckus for no reason!

Qing suppressed her impulse.

So, Qing suppressed her restless heart and lay down on the floor.

As I lay on the floor, staring at the patterns on the ceiling shimmering in the sunlight, Chen Changming wriggled and crawled into my side, hugging me tightly.

And then, Murong Juhee carefully sat down at the bedside and placed Qing's head on her thigh.

As Qing looked up, Murong Zhuxi somehow avoided his gaze and made excuses.

"Because the floor was hard……"

"Hey, you don't have to do that."

In fact, the floor was hard, but the head of the blue was harder than that.

If Qing lies down with his head on the floor, it will be the floor that's uncomfortable, not Qing.

What kind of iron head was that, like an eternal iron, weighing you down?

That doesn't mean that Qing necessarily avoided the favor.

It wasn't that it was uncomfortable to lay my head on the stone floor without a pillow, but it wasn't comfortable.

But how comfortable are the thighs?

The disciple and the teacher, Tian Yuxue, also lay down with a bundle on his head.

Because the guiding principle of Cheon Confucianism was that when you rest, you should rest properly rather than in a half-hearted manner.

Even in the midst of all this, Nan-gong Shencai, who was training, was alone in the cave swinging his twin swords, or rather, his own two swords.

It was at that time that I was enjoying a peaceful break.

I was hungry so I ate a few rice balls.

And then, Murong-ju-hee's hand carefully stroked my hair.

I was enjoying the vibrations of JinChangming snoring loudly while resting his head on my shoulder, and somehow, um.

I'm sleepy…….

It was when Qing was dozing off comfortably.

The sound of footsteps tapping on the floor suddenly brings me back to my senses.

What the heck? Why am I so spread out?

What kind of trickery was this?

Of course, the Blood Cult technicians watching are aggrieved.

The technician from the Blood Offering unit, who was looking at the guys lying down in a mess with the sign saying "rest" written on them, had a heavy head and his blood pressure was skyrocketing.

The reason why the blue was so widespread was because it's the type of person who wants to sit when standing, lie down when sitting, and sleep when lying down.

And once one person spreads it, the original atmosphere tends to become contagious.

Moreover, it was not only Qing who was disguised, so even though they were in a group, they could not shake off the liberation and sweetness of anonymity.

So, a peaceful time continued, with the blood pressure of the watching Blood Cult technicians soaring.

Everyone was enjoying their break in their own way, and since they were hungry, they went out for lunch.

Then came the sound of footsteps.

The group, who were enjoying a peaceful rest after lunch, suddenly came to their senses and followed the sound of footsteps.

Soon, a group of unmanned people appear from a passageway in the cave.

The number was six.

Judging by his uniform, he must have been somewhere. Anyway, he must be one of those bad guys who were taking over a village.

It seems that there are injured people among them, and an unmanned vehicle carrying a comrade stands out.

It seems like I've fallen into a trap.

When the unmanned soldiers discover the Qing party, they are startled and draw their weapons.

He pointed with his finger to the signboard above the closed stone gate that said "Rest."

The unmanned soldiers stood there with strange expressions, unable to do anything, and when the Qing party showed no response, they gathered together and took a seat in a corner.

Starting with him, drones emerge from other passageways at short intervals.

As there are five passages, the number of people in the cave gradually increases.

The Qing party was the first to arrive among the groups of ten, and they had quickly broken through thanks to the human bait and slave, An Yun-juk, so they had time to rest leisurely.

The poor ones were the last group to come out of the last door.

When the last unmanned vehicle came out-

thud!

Above the closed stone gate, a sign that said "Rest" fell down on its own, making a loud noise.

The last group entered the next phase without even enjoying the sweetness of rest.

People's attention was focused.

Then, a new sign hangs from the ceiling above on a string and comes down.

"Fight and prove your worth as the master of the divine art. The gate will open only when twenty-one hearts beat."

Qing furrowed his brow.

Huh? Are we going to kill each other from now on? All of a sudden?

But if it's twenty, why was it twenty-one?

Anyway, the conditions for the door to open were clear.

In that cave, tension begins to slowly build up.