\chapter{Break through the door and head towards the stars (8)}

As you enter and walk straight ahead, a fairly large stone chamber comes into view.

There were several groups of unmanned people there, separated from each other, staring intently in this direction.

Then, soon, with a look of disappointment on their faces, they each go back to their previous conversations.

What was it? What was it?

Qing looks around the stone chamber.

A group of Sapa guys who were clearly the Iron Blood Sword Heaven, and a few guys who were gathered in groups of two or three just watching.

And, um? What was it?

Qing discovers a unique group in a corner.

One man was on the floor on his hands and knees, while the other was kneeling and leaning awkwardly against the wall behind him.

And wouldn't he sit down on the prone guy as a chair, and lean against the back of the guy kneeling against the wall as a backrest, and sit comfortably with his legs crossed?

And in front of him, a man was kneeling, holding out a goblet with both hands.

The woman takes a sip of tea and then places the teacup on top of it.

Clearly, she was a woman who was like Joayo.

A name you can't forget once you hear it, no, was that nickname Joayo?

Anyway, it seems like it collapsed at the west gate and then came down to the south gate.

But what was it? Is she the daughter of a powerful family?

As Qing was unable to hide her bewilderment, Joayo turned her head and met her eyes.

Then, he looked left and right, glanced at the group, and nodded.

"Hey, ma'am. Are there five of you there?"

It's a blue jacket with a face mask turned inside out.

Although Qing was a familiar face, it's the first time for Joayo.

"Oh, right?"

"That's great. We can go together. You know me, right?"

"Aren't you Miss Jo?"

Qing tried to pretend to know.

However, I couldn't quite remember whether Joayo was a name or a nickname, so I just took a picture.

"……It's Lee Hye-hye. Joa-yo was my nickname."

I guessed with a 50/50 chance, but I got this wrong.

I thought the name would be Joayo and the nickname would be Subscription, but unfortunately, I was wrong.

"Anyway, do you want to go with me?"

Then one group got angry.

"Wait a minute, young lady, isn't this promise different!"

There were four men huddled together next to him.

Then Lee Hye-hye shakes her head.

"I'm sorry about that. But women have a way of communicating with each other, so female warriors should help each other and live together."

The men's faces turn red at that.

I know it's just a ladies' story, but to sum it up, isn't it that I can't trust you four men?

"Wait a minute. Where are you going?"

"Oh. Okay. Look over there."

Lee Hye-hye points to a corner of the stone chamber.

There were openly made door frames hanging down, and each stone door was blocked inside.

Five of the stone gates are marked with large scissors, and ten are intact.

And the writing on the wall.

"Ten people form a group and open the door."

"The door opened when ten people stood in front of it. Everyone was waiting because the number of people didn't match. What do you think? If you and I go together, we only have to save one person."

"No, what was that?"

Qing continues to be dumbfounded.

What kind of ride was this? An escape room? What was it?

Enter in groups of ten.

Anyway, they had to match ten people, but they didn't want to part ways with the group they came in with, so they just kept waiting.

Of course, it was only natural that no one would want to enter such a suspicious tomb with a stranger.

"Let's exchange opinions for a moment."

Qing gathers the opinions of his group.

"Um, what should I do?"

"If you have to fill ten people anyway, wouldn't it be better to just pick up the ones that are individually there and fill them?"

It was Nan-gong Shencai's opinion.

Wouldn't it be better to gather one or two loners and make a group of ten instead of a bunch of guys?

Then, even if a fight breaks out, you can gain the upper hand by one or two points.

Even if there was no fight, it will naturally become a situation where Qing and his party lead everyone.

"I wish I could, but would they go with us? And it's better if they stick together. Even if they try to trick us, they'll probably plot amongst themselves."

A person who was alone can make decisions on his own, even if he makes a fuss, and as long as he takes care of himself, that's it.

Those two guys can plot anything they want.

In that case, it would be easier to detect the fact that the people with a large number of people would have to agree with each other even if they tried to talk nonsense.

One vote for gathering loners.

And I vote for merging with Joayone.

Qing looks around at the rest of the group.

"I'll do whatever you say."

Chen Changming gives up his precious vote.

Thanks to this, Qing got two votes.

With this, whether to gather the loners or go in with Joayone, the moment Qing chooses, the decision was made with more than half of the votes in favor.

In other words, Murong Zhuxi has no right to speak.

But wouldn't it be disappointing if I didn't ask?

Qing looks at Murong Zhuxi with that thought in mind.

But at this crucial moment of decision-making, Murong Zhuxi was distracted.

It was Murong-ju-hee, staring intently at something with a gaze that seemed somewhat envious and somewhat filled with warm yearning.

Qing follows that gaze.

The object of Murong-ju's gaze was none other than Jo Ah-yo and Lee Hye-hye, who were sitting on the human chair.

"That, Miss Muyang?"

This was the biggest problem with pseudonyms.

That even if you call me, I don't understand.

This was especially true for newly created pseudonyms.

"Lady Muyang. Now, Lady Muyang?"

Qing teases Murong Zhuxi.

Only then does Murong Zhuxi suddenly come to her senses.

"Oh, me, me?"

"What are you looking at like that? Do your legs hurt? Lady Muyang, you want to sit there too?"

"No, no, not you. Oh! No! It's nothing, nothing. Oh, but if you have any requests for me, please feel free to ask me anything. No, just tell me."

"Hmm."

You weren't listening at all.

Qing looked around the stone chamber.

Aren't all the warriors inside the stone chamber looking this way?

To be exact, it was aimed at Murong Zhuxi's chest.

Unfortunately, it's nothing more than a fake illusion, but how could men know that unless they had clairvoyant powers?

Some people openly and blatantly show their sinister gazes, while others pretend not to look but keep glancing at you.

Compared to that, Joayo's three followers are doing their jobs without even a hint of hesitation, whether they are people or furniture.

Qing quickly made up her mind.

"Let's go with this young lady. Then there will be nine of us. I just need to save one."

And then, Qing walks forward briskly and without hesitation.

It was directed at the guys who were sitting on the floor in one corner of the stone chamber, intently looking at Murong Juhee's huge prosthesis.

As Qing approaches, the men look up with blank expressions.

"What's going on?"

"Oh. Don't worry about me. Just rest. I just need something."

And then, Qing grabs one of the guys' hair and pulls him apart.

It's a natural hand movement, like picking up an object.

"Whoa!? What, what was it!?"

"Don't move! Your balls will fly off."

"Huh."

The man, who was struggling in surprise, shut his mouth tightly at the cool sensation on his Adam's apple.

"Wh, what are you doing!"

"Let go of my brother!"

The startled men, the rest of the Ganyangsa Dogs, jumped up and drew their weapons.

The third was after it came under the control of the Qing.

Qing shouts while holding a dagger to the neck of the third son of the Geonyangsa Temple.

"Miss Jo! What are you doing? Get ready to go!"

"Huh? Me? What, what's going on? And Joayo isn't a name, it's a nickname—"

"Okay. There are five of us, and Sojourner Jo's family has four! We've picked up one, so let's go quickly!"

"No, what if you just grab anyone like that-"

"So, you're not going? You're not going with us? You're abandoning women? You're abandoning women? Didn't Miss Jo say she'd rather have a woman around?"

"No, I'm going. And I'm not Miss Jo, I'm Miss Lee—"

"Woah, woah, don't move. Hey, what's your name?"

"An Yun-juk, it's An Yun-juk."

"Will you come with me? Or will you go to the afterlife? Will you come with me, or will you die?"

"I'll go! Please, at least save my life-"

"Okay! You heard? An Yun-juk was coming with us. You guys stay here, and we'll go find treasure."

The three older brothers of Geonyangsa Dog were greatly shocked when their third son was taken away in an instant.

Well, he suddenly came and snatched the third child away and started a hostage situation, so I couldn't help but panic.

Meanwhile, the third one was dragged away.

Only then does the big guy yell.

"What the hell was this! Can't you hand over the third child right now!"

Qing asks him again.

"What if you don't like it? What if you don't give it to me?"

The large dog of Geonyangsa Temple opened its mouth wide.

Well, I have nothing to say in response.

"If you let go of the third one right now, I can pretend this never happened and move on—"

"What if I don't let you go? What are you going to do if you don't pretend it never happened?"

"Uh, that……"

"Well, you have nothing to say, right? And Mr. An So-hyeop here wants to come with us, too. Mr. An So-hyeop, right? You really want to come with us, don't you?"

"That, that's right! I'll go with you, so bring me the knife—"

"Okay. Agreement complete! Hey! Don't move."

As Geonyangsa Gyeon takes a step closer, Qing holds his sword close.

"Eek, brothers! Don't move!"

An Yun-juk was startled by the blade pressing against his Adam's apple and tries to stop his brothers.

Then, Qing takes the hostage and drags him away, then slowly retreats.

So there was one hostage.

One hostage taker and his companions.

And ten people, including Joayo and her followers, gathered in front of the stone gate with complicated expressions, wondering if this was right.

Then, with a trembling sound, the stone gate slowly disappeared upwards.

While the rest of the Geonyangsa Temple were stamping their feet, unable to do anything, the Qing party and the rest disappeared inside the stone gate.

And then, bang.

A new stone gate falls down, blocking the entrance.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Lee Hye-hye has a complicated head.

The reason I suggested going with the Qing party was because the group itself was much more gentle than the group of dark-skinned men.

But now that I look at it, what the hell was going on? Didn't they fill the remaining spot with an unimaginably radical method?

"Hey, what are you thinking?"

"But there's one empty spot."

"Wouldn't it be okay if I just accepted one?"

"Hey, if someone were to crawl into a place like that alone, they'd probably be pretty confident in their own abilities. Wouldn't it be better to just grab someone and bring them instead of going in with a pro like that?"

"Huh?"

Lee Hye-hye tilted her head.

Now that I hear it, it seems like it might be true.

"Since you gathered ten of them, there must be a reason for cutting them. Doesn't An So-hyeop's expression soften? Anyone who sees him would think you brought him here by force."

At that, An Yun-juk's expression suddenly turns sour.

Qing just burst out laughing.

"What's wrong with your expression? Why, you don't want to go with us? Then what can we do? Okay, An So-hyeop was free now."

"What was that……."

"I won't hold you back, so just go. Why would you hold on to someone who doesn't want to go with you?"

What good can it do if you say you are free now?

After being dragged in, the stone gate was blocked and there was only one way.

An Yun-juk's shoulders slump.