\chapter{Break through the door and head towards the stars (7)}

In front of the alumni association.

Qing shouts cheerfully.

One of the inner powers was a very cold and overflowing blue.

Even if you indulge yourself in the luxury of filling your inner energy with every scream, there will still be some leftover inner energy.

"Everyone, now was not the time to be doing this. Those at the South Gate, West Gate, and North Gate are already moving closer, step by step, toward Shingabibo!"

Qing shouts in a sorrowful voice.

The warriors who had been surrounding him with their backs to the gate and blocking him could not hide their anxious eyes.

"In a situation like this, can you be the only ones left behind!? Everyone, join forces and knock on the door!"

Qing appeals that the door must be broken down.

Originally, I was planning to use the one-hit-kill door-smashing strategy once more and then head towards the south gate.

But, in the alumni association, weren't they divided into front and back instead of left and right and facing each other?

Thanks to this, the one-hit-kill sword and rain combination strategy was blocked.

Even if she was a superhumanly strong woman named Qing, she cannot strike if she cannot reach the door.

So what?

We should at least try to appeal (agitation) verbally.

And the Qing's appeal (agitation) was already at a level far beyond that of Zhongyuan people.

Because the people of Zhongyuan are, in a bad way, stupid, and in a good way, naive.

Indeed, in Qing's hometown, propaganda and fraud are, to exaggerate a little, a daily occurrence that we encounter dozens of times a day.

Compared to the Qing, the people of Zhongyuan are a people with a severely reduced immunity to propaganda and agitation.

"Cheonseungnim? What if all the other doors are really open?"

"Nonsense. That can't be true. Da Yeoreum? Anyone who hears it knows it's a fake name. He must be a saboteur sent from another gate to destroy our stone gate."

"But, if by any chance it's true…"

"This was a single, unfalsified truth! The door opens to those who knock! The path was not something you wait for, but something you must forge yourself! This speaker! Shout it out loud!"

However, they are still just observing, and there was no movement to break the stone gate.

The blue became urgent.

In a little while, people will be rushing in from the collapsed north gate(?).

Qing, who was feeling anxious, started to spit out random words.

Qing's specialty was talking nonsense that doesn't even make sense.

"Everyone! Please give this Da-yeoreum just one chance! Countless doors have already opened in front of me, and thousands more have opened in front of Da-yeoreum to welcome me!"

Well, since Qing has lived in a world with automatic doors, he must have encountered a door that opened when he stood in front of it once or twice.

But the gaze of the audience was cold.

Now I'm sitting down and the door was opening automatically.

Even the gazes of those who had been wondering if other doors had really opened are now growing cold.

"Everyone! A swordsman who has reached the pinnacle of perfection wields the sword of his heart! Likewise, this Organ-Won-Jeon-Je-Sin, who has reached the pinnacle of organ-wielding, has reached the realm of manipulating the organ of his heart! That was why I am the Organ-Won-Jeon-Sin-Je! Do you not understand the profound respect contained in such a title? The best engineer in the world! That was who I am!"

"Hmm?" "Huh?" "Doesn't that make sense?"

A few thin-eared drones flutter about.

What if a warrior who has reached the pinnacle of perfection could build a weapon with his mind?

Can't a highly skilled engineer build an engine with his mind?

How great would it have to be for all of the best formulas of King John Shin Je to be included in the nickname?

But among them, there were only a few people whose ears were flapping, a very small minority.

No matter how naive the people of Zhongyuan are, they are not to the extent of believing just any nonsense.

The gaze was getting colder and colder.

Qing spits out fire without paying attention.

"So, this summer, I've reached the supreme state of opening all the doors! Because I live by holding onto all the doors! I live by holding onto them tightly! Holding them tightly like this! Door, won't you open right now? If you mess with me, I'll kill you, I'll smash you to pieces. I live by holding onto all the doors tightly like this! When I say, "Hey, open right now!"—"

That was exactly when.

Nine Palaces… … !

A strange vibration, like a heavy mass weighing on you, rises from the soles of your feet.

Those are the drones that turn their bodies at once.

"Hey, Seokmun!?"

"It's opening, it's opening!"

It was just like the people's cries.

With a vibration that seemed to shake the entire mountain, the huge stone gate slowly sank downwards.

The drones slowly turn around again.

There was a hint of distrust in those eyes, but not distrust in a bad way.

It was a disbelief in the mystery of what great wonders, how on earth do they exist?

And the rest of the eyes sparkle with wonder and admiration.

"It's really Da-yeon, Da-yeoreum."

"I believed in you!"

"The mind sword, no, the mind organ, the realm of the mind organ!"

"The King of Machinery!" "The King of Machinery!" "Summer!" "Summer!" "Summer!"

In an instant, there were people who called out Da Yeoreum and that ridiculous nickname.

No, what the hell? Why was it open?

But now, why can't I just open it and close it? It's not something I can do.

Qing raised her hand in a flash.

The cheers that echoed around him.

"Everyone! I've done my part, so I'll be leaving now! I'm Da Yeoreum! If there's a closed door, please ask Da Yeoreum of Zhangjiajie!"

Qing finishes up whatever comes out and turns around in a hurry.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Chen Changming, with sparkling eyes, gives a thumbs up.

"It really opened. It's amazing."

"No, I, uh, I don't know either."

Tian Yuxue snorts.

"Hey. What if I really open it?"

"What do you do when it's open? I didn't know it would actually open when you told it to."

Qing was being treated unfairly.

What the heck was it that makes it open? Does it really open?

Does it open with voice recognition or something like that?

Such technology in this uncivilized ancient China?

But, thinking back, maybe that could have been the case.

If we apply the mysterious energy of the universe, wouldn't something happen somehow?

Why, didn't that method just make people flounder in illusions?

It was a mysterious miracle in itself, to the point of even showing the painful wounds of others in the form of images.

"Hmm. I guess I figured out how to open it without even realizing it. What should I do, this genius?"

"Ha. What can we do with something that's already open? Let's just block the south gate for now. But if there's only one exit left, wouldn't someone with magic eventually crawl out through there?"

Tian Yuxue was not the type of person to meddle in things that had already happened and to try to explain the truth.

Besides, it wasn't something the disciple did on purpose.

It was just an unfortunate accident, so what's the use of blaming him more?

"You can't go to Nammun in the summer, right?"

"There will probably be guys coming down from the west gate, so it'll be difficult to use it again."

Hasn't Dasummer already come out three times?

Originally, no matter how satisfactory and effective the method was, it had to be satisfied with three times.

Why, isn't there a separate name for the first, second, and third sections?

"sure?"

"There's a way. Anyway, since we've confirmed that the door will collapse if you try to trick it, let's try inserting a fake heart this time."

The career of a shaman, or the career of a pseudo-pharmacist, which was a hobby and side job of Tian Yuxue, shines.

Operation: Insert a fake heart!

First, Nan-gong Shencai unleashes his sword energy to prove to everyone that he was a true warrior.

Two. The rest of the group pretends to betray Nan-gong Shencai and attacks him, taking out his heart.

3. Place the fake heart prepared in advance in the center of the stone gate in place of the heart.

Fourth. The stone gate that swallowed the fake heart crumbles down. Perfect!

So the group hides in a secluded mountainside and performs a con play.

Once the facial features are known, the disguise must be removed.

However, it's a disguise that has already been changed twice.

Besides, Da Yeoreum ended up selling her face too much.

"It's over. Your face was so swollen that it's hard to get anything done no matter how much you try to add. But if you let your chest down, how many women in the world are that big and skilled? So."

"Wow! Inpimyeon-gu!"

It was finally the moment when Qing got his hands on the legendary disguise tool, the Inpimyeongu.

As Qing-i looked back and forth at the drooping face of the man, Tian Yuxue burst into laughter.

"What's so great about that?"

"It's amazing. I've always wanted to try it."

"Huh, once you try it, you won't want to wear it again. First, wrap your head with this. Loosen your hair and tuck it inside your clothes."

First, wrap your hair tightly with something similar to a net, and hide the long part by tucking it into the back of your neck.

And then put a cow's stomach on top of it.

Qing already realized that something was seriously wrong here.

What? I'm already feeling suffocated.

Why do they put something like a contraceptive device on people's heads?

And only then do you turn the face mask inside out.

The inpimyeongu was structured to spread wide down to the nape of the neck and be tucked inside the clothes.

The feeling of being stuck to your face was so uncomfortable that it's beyond words.

I'm already sweating.

Qing, unable to bear it any longer, uses Hansimgong.

Then the face starts to get bumpy.

"Hey, are you planning to brag to everyone that you're wearing a human face mask?"

"I'm screwed……."

Qing sat down with a vain expression.

This isn't it. This really isn't it.

And then you have to get a fake heart.

While Tian Yuxue was away hunting a suitable animal, the group got together and prepared their lines.

So, about half an hour later, when Tian Yuxue returned, the situation had already been resolved.

In particular, it can be said that Nan-gong Shencai's passionate performance, in which he pours out his heartfelt sorrow after being betrayed by a colleague he trusted, was outstanding.

And hehe, the acting of Qing, who gave up his comrade's heart in a mean and vile way!

It was so natural that everyone wondered if it wasn't acting but their true nature.

So, Nan-gong Shencai puts the bag containing the boar's blood and heart in his pocket and puts them together one last time.

It was a thorough preparation that gave off the air of a professional fraud group.

However, this performance was never actually demonstrated.

Well, that's because the south gate was already wide open when the east gate opened earlier.

So when the Qing party arrived at the South Gate, only the hole that had been the South Gate was already wide open.

"Is it open?"

"It's open……."

"Hmm."

"I prepared hard for it……"

Of course, that doesn't mean I didn't question why it was open.

"Hey, I guess it's too late."

I thought those impatient guys must have taken someone's heart and offered it to me.

The grand plan to destroy all entrances and bury the absorption magic in the mountain also failed.

So, I had no choice but to go in and take a look.

I thought it would be a bit more comfortable… … .

Around the southern entrance, a group of unmanned soldiers huddled together, glaring at each other with fierce eyes.

However, he only shoots a glance.

Not all unmanned vehicles enter the Shingazimyo.

The plan was to wait outside and target the guy who brings it out.

Of course, since there are multiple entrances, even if you wait, you may not come out this way.

Since I didn't know when it would come out, I just had to keep guarding my position.

But wouldn't it be better to be outside than in a tomb where you never know what dangers might lurk?

So, no one can stop the Qing party from rushing into the Shingazi Temple.

So, the entrance to the Shingazimyo Temple begins.
