\chapter{Break through the door and head towards the stars (12)}

The room was a veritable crucible of shock.

Who was Taesan Demon King!

The master of the method of Unrestrained Realm's review!

Jaw-beop was a branch of martial arts that involves attacking by clawing with the hands, and Taesan Demon King was the best master of this art.

It was said that if you wave your hand, the human form will be shattered into pieces, so it's called Taishan!

Although he was a great demon leader who was called a devil because of his eccentric personality and his cruel hands that tear people apart.

The person who was most shocked was Lee Hye-hye.

Although it's a bat-like technique with half iron fist and half weapon, it's a technique that has been practiced.

Didn't the head of the senior who was at the forefront of the law get torn off?

The people of Zhongyuan look down on martial arts.

Even the martial artists were divided among themselves and hated each other.

First of all, there was martial arts at the very top.

The ultimate goal of martial arts lies in the fist, and the martial arts are the true path of a martial artist, according to martial arts experts.

If anyone asks about the greatness of martial arts, let them look up and see Seung San!

In fact, this was a good excuse not only for the martial artists, but for all Zhongyuan warriors.

Even the martial artists who ridiculed the primitiveness of martial arts would keep their mouths shut and only grumble inwardly when told to look at Sungsan.

This deadly kid was learning martial arts without any foundation, yet he dares to talk about Shaolin.

Below that's the method.

In the Buddhist law, there are many divine beings under the famous Tathagata God.

In fact, this was because of the internal pressure method, which was the ultimate in pure qigong, and it's most advantageous to use the palms, which are the most efficient passageway connecting to the danjeon.

Of course, the peak of the Imdok Yangmaek, Jeongsu-ri, can produce the most powerful output.

However, Jeongsu-ri was a critical point called Baekhoehyeol.

If you get hit right, a fate worse than death awaits you: you become a fool, a retard, and a moron, and end up shitting on the wall.

Of course, it's a place protected by the strongest bone in the human body, but wouldn't it be too ugly to use the crown of the head as a martial art?

And the golden method that puts competent steelmaking first.

There are powerful techniques that can be used from a long distance.

And among the martial arts, the one that was rated the lowest was the method of making.

Each method was not considered a martial art, and martial arts are all techniques used together except for fists.

So, if you just learn the method, you will become the most despised martial artist among martial artists.

Well, the original meaning of an attack with fingers was scratching.

How strong could a human scratch without sharp claws like an animal's?

Moreover, the public perception was that martial arts were fundamentally evil.

Starting with the magician called Gu-eum-bae-gol-jo, even the nobles in the Jeong-sang clan were so murderous that there were not many people who could learn from them.

The reality was that, with the exception of a few witches, there was not a single master who has reached the status of a shaman through pure magic.

So, Taesan Demon Lord, who was about to become Hyeon-gyeong after Hwa-gyeong, was a great senior who gave great hope to the martial artists of the world.

Besides magic, you can also reach the realm of the living through magic!

But that dream was now gone.

Taesanmagun was no longer there.

It was a miserable end, as he was raped by a woman as young as his daughter and ended up with his head cut off.

It was a moment that brought great despair to the world's jurists.

But Qing doesn't know about such things.

If someone complains, I'll just laugh them off.

Hey, a lawyer? Isn't the name too much of a lawyer?

I need to pay attention to my pronunciation.

Taesan Demon Army was somehow a lawbreaker.

But don't be too discouraged.

Still, it's the end of a great martial artist who went the furthest in martial arts.

To Qing, who still finds martial arts difficult, he was just a perverted old man full of evil deeds, whether he was a Taesan Demon Lord or a Hwasan Demon Lord.

What, have you ever seen the process of separating heads in your life as a martial artist?

Anyway, since the group was so excited, how could Qing miss this great opportunity?

The disciples who had been following Taesan Demon King were still trembling, their eyes still trembling, wondering if it was a dream or reality, and were unable to come to their senses.

The Moonlight Sword (No. 10) cuts through the air.

Why did Taesanmagun die?

Because I let my guard down.

Why did the disciples of Taesan Demon King die in a single blow?

Because I let my guard down.

The longer the sword is, the thicker its trajectory is.

Since they are all about the same height, wouldn't they be sticking their necks out just right for cutting?

The heads of three unmanned personnel carriers are caught in the crescent moon drawn by starlight.

A thrilling thrill runs down my spine and spreads throughout my body.

How can I never get tired of this?

Taesan Demon King's remaining disciple was now only one.

Only then does he come to his senses, as the shadow of the sword cuts his face exactly in half.

The blue moonlight sword, which flashed brightly, fell towards Jeong Su-ri with a vicious, sharp sound.

The disciple, in his desperation, raised both hands and blocked the sword's trajectory.

Eight fingers of soft iron, tempered by the arduous external training of the Taesan Bloodline, but not as strong as steel, are intertwined and rise upward.

In that moment, the blue energy suddenly disappeared.

Because he's the type of guy who doesn't need to use his powers.

It was the mindset of an angler who deliberately tried to maximize the feel of the fishing rod with a soft rod.

The sound of iron hitting the ground.

The four fingers of the disciple of Taesan Demon Lord fly into the sky, and the Moonlight Sword was stuck between the fingers.

He held the blade with four fingers, but it seemed he had not anticipated the strength that a human possessed.

The disciple's two hands, holding the blade in a flash, are dragged down to below the dantian.

The disciple, whose face was split open from the crown of his head to his navel, collapses to the floor.

Yeah, this was it.

The knife was so sharp that it lacks the feel of a knife.

In an instant, the corners of Qing's mouth split open, stretching all the way to his ears, as a lightning bolt flashed through his entire body.

However, Qing had a leather mask over his face.

Thanks to that, a monster with a grotesquely twisted lower body and a terrifying smile was glaring at you with a sharp gaze.

"Huh." "Wh, what……!"

Men are dumbfounded by the sight of such a horrific sight in their dreams.

Would the men freeze at the smile of a monster barely wearing a soldering iron? If that's the case, you might want to just throw away the pepper.

But in the hometown of Qing, even a warrior grandfather, let alone a warrior, would momentarily freeze when confronted with a monster-like figure less than human, known as the Uncanny Valley.

"You filthy bastards! I won't forgive you!"

Qing runs out with great momentum.

"Damn it! This!" "Wow! Young lady!" "Sister!"

"Haha! That's right, that's how you should be, no, you're my sword friend!"

Three normal people who were terrified and one abnormal person who was amazed by Qing's inaction followed Qing.

In particular, Nan-gong Shencai was impressed by the Ilgumsamgyeong (three necks with one swing of the sword) and the bamboo splitting that ignored defense.

How can you not be excited as a swordsman!

It was a tragic sight, with only five people charging at a man of nearly twenty.

The group of female warriors behind him also suddenly came to their senses.

Since I only saw the back of Qing's head, the mental shock was much less.

"Damn it! What are you doing!?"

Lee Hye-hye takes the lead in the second wave, swallowing the curses.

And so, a bloody battle breaks out.

This was the moment that the Blood Cult technicians have been waiting for the most!

The technicians who had been manually operating the traps in each hallway gathered together to watch the battle between the drones.

So, everyone puts their eyes on the observation windows hidden under the torches here and there so as not to miss the exciting sights.

If you are a blood cult member, one of the three was either a martial artist, a government official, or both, meaning you have a grudge against the world.

One of the three was a pervert who just gets pleasure from causing trouble.

But when the Blood Offering technicians arrived, the ratio dropped to nine to one, and each of them had bloodshot eyes, just like the gazes of the martial artists who were waiting for the scene where they would fight each other with their swords.

Actually, even if it's not necessarily a grudge, well.

What in the world was more fun than watching a safe fight?

"I wonder if Taesan Demon Lord didn't go too far. Still, he was a strong candidate. Who bet on Taesan Demon Lord?"

"What the heck, what the hell was this Unrestrained Realm review?"

"Oh, it's you. Hehe, you're out early."

"Damn it. But who the hell was that girl? Does anyone know her? Someone who's good at martial arts?"

"Hmm, it seems like the Moon Sword, but I'm not sure. Was the Moon Sword originally such a vicious murderous sword?"

The Blood Offering Technician focused on the Qing swordsman's swordsmanship as he struck, broke, and swayed haphazardly.

Occasionally, the Moon Lady Sword's herbivore was visible, but that's all.

It was a very innocent look, like a child who doesn't know swordsmanship swinging it, or in other words, it doesn't even look like swordsmanship.

Innocent? The Blood Cult technician, touched by this thought, rubbed the goosebumps that ran up his spine.

A vicious murderous act that involves stabbing, pulling out, stabbing, and pulling out, and persistently cutting and dismembering the body's extremities.

A distorted smile that appears occasionally.

Isn't this a decision of innocent malice, like a child playing with a bug?

Then, suddenly, I snatched the rope in my hand and the man who had been sticking his neck into the blade flew backwards with the back of his neck forward.

Thanks to him, the man with the rope who saved his life suddenly gets up, but he was awkward and faces the enemy again, as if he was obviously a weakling.

Whenever he was in danger, the Moon Sword wielding Salsung pulls the leash to save him, so instead of fighting, he just rolls, rolls, and backs away, and when he was in extreme danger, he gets caught in the leash and flies into the sky.

It's a miracle that he can cut people to pieces with one hand, and it looks like he has eyes on the back of his head.

"Madhu? There's no way such a vicious female Madhu wouldn't be talked about. Isn't she close to us?"

"Why would we interfere in the grand scheme? Like the Demonic Cult?"

"How can you put a map in a demonic cult? It takes a year just to get there and back. Hmm? That kid you came with was definitely a martial artist of Jeongjong's. Why would a kid from the Jeongpa be hanging out with a savage like that? The rest is, um, ambiguous."

Even from a cursory glance, it's clear that one of the particularly small children has trained in the martial arts of Jeongjong.

But what about the rest?

A large woman, holding twin swords, calmly guards the boy's side, while an unidentified middle-aged man also appears to be guarding the two, but was not very active.

However, the man among the group who was wielding twin swords kept laughing and talking about something.

"Surprisingly, there wasn't much of a fight, was there? Joayo really lives up to its reputation."

To be exact, it's not Joayo, but Joayo's three followers who are truly worthy of the name.

In fact, Lee Hye-hye was more famous for her funny followers than for her funny nickname.

Those three followers who call themselves Lee Hye-hye's slaves.

In fact, he was a master one or two levels above Lee Hye-hye.

Rumors say that Lee Hye-hye was actually of a very noble status and that her escorts are hers, or that Lee Hye-hye's secret arts reached the heavens and she captured three men in the hem of her skirt.

So, the situation quickly shifts in favor of the exploration team accompanied by female warriors.

It was a very regrettable situation for the Blood Cult technicians.

I wish we had fought more evenly and had suffered minor and major injuries even though half of us were still alive.

There could have been some interesting things to see, like abandoning the injured to overcome traps or using the injured to clear passages.

"Wait a minute, numbers! Isn't there twenty-one left? One, two, three, four…"

"Where was the time to count! Open the door! Open the door!"

The blood cultists, who had been watching in a daze for a while, lost track of their time and suddenly rushed towards the institution.
