\bookmarksetup{startatroot}
\addtocontents{toc}{\bigskip}
\chapter{First Crisis, Afterword}

Outside the Heavenly Demon Tomb, it was already a dark night.

Qing stretched vigorously.

\textit{Phew, I thought I was going to die trying to keep up appearances.}

In truth, the urge to run away straight down the stairs had bubbled up several times during the ordeal, but well, somehow she had managed to carry it out splendidly and survive.

As relief and the joy of survival washed over her, Qing unconsciously got excited and performed the most successful dance in human history while moving backwards.

It was the signature move of a certain Mr. Jackson from Indiana. The Moonwalk.

The principle that the Heavenly Demon had demonstrated with his body remained, making it the most precious of the insights Qing had gained.

And as she was celebrating with this victory dance...

"Ahem."

Qing was startled by the coughing sound.

"Shit, you scared me. Gramps. Why did you follow me?"

"I packed your belongings to give to you when you leave. Even if you are leaving, shouldn't you at least take your own things? You careless child."

"Wow, really? You packed everything?"

Only after hearing this did she remember about her luggage.

Starting with the Yangtze River Free Pass, all the Guest Plaques her friends had given her, and wasn't there also a letter from her Master to give to the Emei Sect's Grand Abbot?

Come to think of it, the old man's words were true.

If her personality had completely changed, the attention given to Qing would have disappeared along with it, and since he had even packed her luggage, he must have intended to let her go willingly after she opened the door by blowing the Fushen-di.

Qing followed behind Cui Liweng, trotting along.

Upon reaching a certain luggage cart, Cui Liweng went inside and came out with a bundle, revealing familiar items.

Qing eagerly grabbed the most welcome item among them.

\textit{You're back! My Moonlight Sword!}

Though it had been a while since she held the Moonlight Sword (No. 8), the handle fit snugly in her hand as if it had never left her side.

Qing grinned as she fastened the sword to her waist.

Then, as she was about to receive the rest of the luggage, Cui Liweng held onto it, hesitating to hand it over.

Qing's eyes narrowed.

"What's this about? Is the rest Pay to Win or something?"

\textit{Was this sort of business acumen also a tradition? As expected of OG China.}

\textit{Do I have to pay a price to get my own things back?}

However, Cui Liweng spoke while looking uneasy.

"Ahem. I am old and do not know how long I shall live, so I was thinking of looking for a good burial site. Perhaps... would that be alright?"

"Wait, why are you asking my permission to find your deathbed... No, nevermind. Sigh."

Qing sighed deeply.

Even if she pretended not to understand, it didn't seem like the old man would back down easily.

Saying he wanted to find a place to die wasn't really about reserving a sunny spot with good fengshui facing a mountain and overlooking water.

It was a desperate wish to spend what little life he had left together and die by her side.

"Gramps, let me make this clear. I have absolutely no intention of accepting you as my stepdad. In exchange, I don't care in what way you view me. I'm just going to use you to carry my luggage, pull the carriage, and do all sorts of chores."

Though her words were irreverent, it was ultimately permission.

Cui Liweng's eyes reddened.

"Thank you, thank you. Even that much is too generous..."

If the old man's remaining life could be peaceful just by following her around and taking care of her, there was no reason not to grant that wish.

He had already suffered through his life, and he was too old now to mentally abuse himself by being shackled to the dead.

But if he later came at her with 'You are my daughter' or some shit like that, it would be a case of kindness turning into malice.

She might not care about other things, but she couldn't stand that.

"But. I don't have a hobby of dragging around a Great Demonic Adept and being pointed at by people while traveling. Get rid of that Demonic Art that you can't even control anyway. What if you later go crazy and come at me saying shit like 'Why did you deceive me' and 'Give me back my daughter'?"

It was telling him to disperse the hostile arts he had cultivated his entire life.

Something a martial artist valued more than their own life.

"I shall do so. Right now, even."

Yet, there was not a hint of hesitation in Cui Liweng's answer.

Qing sighed deeply again.

"Let's get out of here first and then talk. If we linger here, all the Demonic Adepts will come rushing in."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Inside the Heavenly Demon Tomb, the Elite Masters of the Divine Cult gathered around Zhi Shengzu.

In the Divine Cult, which followed the law of the strong, Elite Masters were essentially synonymous with the cult's leadership.

"Look, Demonic Brain. Do you really intend to follow that wench?"

"She is the Heavenly Demon of this age. Did you not see her Heaven-Shattering Demonic Qi with your own eyes?"

"That may be so, but isn't she still just a young girl? There is also the matter of the Divine Cult's dignity, after all."

"It is even more splendid because she is young, is it not? Think about the Celestial Martial Emperor. Is it possible for such a figure to exist only in the Orthodox Faction?"

"However, isn't she already a member of the Orthodox Faction?"

"Did you not see her actions? The Heavenly Demon will inevitably have no choice but to return to the cult."

"Hmm..."

The Masters let out contemplative sounds.

Gouging out a living person's eye was not something that could be done without considerable cruelty.

Especially if it was done with a smiling face, not hiding the pleasure, as if playing with a toy - even more so.

"But must we now give up the long-cherished wish we have been pursuing all our lives? Moreover, reconciling with those Zhongyuan bastards. Is that even possible in the first place?"

"It might actually be for the best. Isn't it said that the strong would not get beaten up, even if they act out? What force in Zhongyuan would dare to confront the Divine Cult?"

The Heavenly Demon Divine Cult had already proven its true strength through four Great Wars Between Orthodox and Demonic.

Although they had been defeated each time, hadn't they also left great wounds on Wulin?

Even if the Divine Cult suddenly declared that they would settle past grievances and come out into the light, Wulin couldn't cry out 'What are you smoking?! That's impossible!' and wage a war, voluntarily causing damage to themselves.

"To be honest, how long must we continue to control the fools of the Divine City? Isn't it because of this that we have built up a history of defeat every time we invade?"

The Divine Cult lived hidden in barren lands.

It was because they lacked the ability to support a large population.

Even the gold sycees earned by various departments of the Outer Hall through their 'businesses' in Zhongyuan were ultimately limited.

That was why the Divine Cult had no choice but to follow the law of the strong.

Thus, the Divine Cult's law of the strong served as a means to maintain a limited population while building the most elite forces possible.

Ironically, the natural enemy of elite forces was a vast quantity of ordinary people.

Even if they could overwhelm them with irresistible battle records and achievements, the loss of each individual was painful.

The longer the war dragged on, the more overwhelming the military achievements became, but the more unfavorable the war situation became, ultimately leading to defeat and retreat.

No one present was unaware of the harmful effects of the law of the strong.

After all, everyone had gotten here by devouring others.

But even knowing the severe side effects of the law of the strong, what could they do when that was simply how things had to be?

Moreover, its results were impressive.

Although Qing had constantly criticized them as retards without a single redeeming quality, the truth was that there was no group in all of Wulin as powerful and unified as the Heavenly Demon Divine Cult.

The Masters looked very unenthusiastic.

That was because most of them were people who had been pursuing wealth and power after the liberation of Zhongyuan, just like in their illusions.

However, Zhi Shengzu was the Secret Pavilion Leader and Demonic Brain, respected by the Divine Cult despite his terrible martial talent.

Given enough time, he was confident he could easily manipulate these uneducated Demonic Adepts who only respected strength.

It wouldn't be difficult for the Heavenly Demon Divine Cult, which controlled the Silk Road, to proudly claim its territory and achieve even greater prosperity than now by adding governance that combined doctrine and morality.

Zhi Shengzu swallowed his ambition inwardly without showing any expression.

In the past, a general named Ci of the Taishi surname had said. (For reference, his name wasn't Lion.)

'If born as a well-built and manly male, shouldn't one wear a seven-chi sword and climb the stairs to the Son of Heaven?'

One who could dare to wear a sword and stand beside the Emperor.

Above all men and below only one, it would be the highest position that a schemer could reach.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Supreme had no name.

He had never seen his father's face, and all his mother had given him was bitter hatred.

In other words, all he had received was indifference and hatred.

He hadn't even been given a name.

However, the Supreme wasn't dissatisfied with this fact.

The Supreme didn't need a name because he was the one and only Supreme.

If there was only one Supreme in the world, there was no need to use a name.

But now he knows another reason why he had no name.

He was just a vessel for the Heavenly Demon's soul to settle in.

There was no need to give him the luxury of a name.

When he realized this fact, the Supreme simply fell into despair.

But no longer.

For the first time in his life, he learned the pain of being scolded.

And also for the first time in his life, he felt that caring touch that stroked his head.

He heard the mercy of being forgiven.

He could clearly recall, even with his eyes closed, that genuine smile coming from within, that sincere pleasure he had never known before being directed at him.

This was the love that parents bestow upon their children.

Yes. That's right.

Can those who irresponsibly create a body and carelessly throw it into the world be called parents?

The qualification of parents lies in that very affection.

Age, beauty, and even gender didn't matter in this; wasn't that why humans simply call men fathers and women mothers?

But there was still one thing left.

The most precious thing parents give to their children.

Something the Supreme still didn't have. A name.

She told him to be good, so he will be good.

When they meet again, with that promise, he will finally receive a name.

The Supreme looked at the elites of the Divine Cult.

They were insolent bastards, busy whispering among themselves while daring to leave out the Supreme.

Anger boiled up in the Supreme's heart.

That wrath became strength, and black Demonic Qi seethed.

The Supreme was a martial artist of threshold of the Profound Realm, and even that was merely something he had restrained himself for the sake of Demonic Descent.

When his dantian was shattered, those restraints were also released.

As such, it resulted in the entry into the Profound Realm.

With that enlightenment, he forcibly patched together his shattered dantian. Even if the result was nothing more than a rag, he somehow managed to preserve it.

His body was one prepared for the Heavenly Demon.

The medicinal properties of the Elixirs he had consumed instead of food since childhood still flowed through his four limbs and hundred bones.

As long as the shape of the dantian was maintained, recovery was not impossible, just time-consuming.

The Supreme calmed his anger.

It wasn't such a difficult thing to do.

Just recalling the smile etched in his heart was enough.

His mind and body naturally settled, and his mouth unconsciously relaxed into a smile.

\textit{As you said, I'll be a good boy.}

\textit{My beloved…}

\textit{Mother.}

This was the Supreme. Aged forty-seven years old this year.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Sometimes, a person's Upper Dantian opens, allowing them to unconsciously read the workings of heaven and earth.

This was called the sixth sense, or a premonition.

Qing shuddered.

Suddenly, she had a really, really bad feeling.

\textit{The fuck is this? I just got goosebumps all over.}

But no matter how much she thought about it, there was no particular reason for such foreboding.

Qing just kept mulling over the uneasy feeling.

Well, of course she would.

After all, how could she possibly know that she had just gained a grown ass son in addition to a father and an older sister?