\chapter{Heavenly Demon Tomb (7)}

The Demonic Adept who took down Shaolin Temple's signboard and put up the Heavenly Demon Temple's sign was said to be a Guardian with an affiliation to the Shrine.

This individual had sailed across the vast ocean leading dozens of ships. As such, he couldn't be identified because the command ship was far away, and Cui Liweng had no idea who it was either.

But in Qing's eyes, he seemed like the manliest man in the Demonic Cult.

It was truly a journey over mountains and across seas.

Whether it was luck or not, they finally managed to encounter the only small boy among the Demonic Cult Masters.

"Yo. Kiddo."

"...?"

Zhi Shengzhu's eyes widened.

Given that Zhi Shengzhu usually had no expression, one could roughly guess how surprised he was.

"What? Why are you so surprised? As if you've seen someone you shouldn't."

"You... you're alive?"

"What do you mean 'alive'? Since when did I die?"

"I clearly saw your corpse. And it was in a place modeled after the front yard of the Divine Cult's Holy Fire Hall."

"Holy Fire Temple?"

"It is the mansion where the Great Guardians reside. It seems someone wants to kill you badly enough to create an illusion of your death. Be careful. Even though it is an illusion, they might try to kill you if they see you."

For reference, this conversation completely left out one person.

Cui Liweng cleared his throat.

"Ahem."

"Purple Lightning Demonic Warlord, you are safe too. That is a relief."

"I heard the Demonic Brain was trying to remove the Formation, so I came to help. How is the progress?"

"I have removed a few cornerstones, but I cannot even begin to fathom how many were laid down. For now, I have applied the Nine Palace Method to the Eight Trigrams and used the Dissolution Mountain, but..."

"I see. As I was coming, I saw the Imaginary Heaven's Peerless Time with the Terra Vital Road."

"Ah, then in the Southern Heaven Section, we just need to remove the four similar methods of Spirit Trigram, Spirit Sky, Emerging River, and Flying Array."

Some kind of extremely professional terminology was suddenly unleashed.

From that point on, it was the start of a conversation Qing couldn't understand at all.

Of course, she had no intention of helping anyway.

So she soon lost interest and looked around, but there wasn't anything particularly interesting to see.

In the end, the bored Qing let out a long yawn.

Seeing this, Cui Liweng clicked his tongue.

"Tsk tsk, are you trying to split your mouth like that?"

"What else am I supposed to do when I'm sleepy?"

"Then you should just sleep properly instead of gaping your mouth so carelessly like that. You are a grown woman. If you had married early, you could have been a mother by now."

Qing tilted her head.

\textit{Isn't this nagging familiar?}

\textit{Do all old people become like this?}

But Cui Liweng wasn't actually, nor deserved, the role of such individuals.

Qing frowned hard.

"Boohoo, who cares? Or more like, why do you care? What does it matter to you whether I become a mother or a father?"

"Your language is so filthy, girl. How have you become more and more vicious like this? Is it because you are relying on your pretty face?"

"Forget it. So, how long do you think it will take?"

Cui Liweng looked at Zhi Shengzhu.

Zhi Shengzhu looked back and forth between Qing and Cui Liweng with a strange gaze. Then, unable to withstand Cui Liweng's silent urging, he opened his mouth.

"I thought it would take at least another day, but with the Demonic Warlord's help, it should be much better. In fact, isn't time pressing since we have no water?"

People could endure without food, but they couldn't last long without water.

This was true even for the greatest of Masters.

Qing calculated inwardly.

Zhi Shengzhu was an expert.

A job that would take a full day alone would be halved with this old man's help, so half a day.

Then, I can sleep soundly, right?

"Since Gramps said he'd do it, I'm going to sleep. Wake me up when the Formation is about to be undone. I want to watch how it turns out."

Qing made sure to remind them just in case, then wriggled around trying to find a comfortable position to rest her head.

Finally, she found a position that felt comfy enough.

It seemed she had already wandered for so long that she had passed her usual sleeping time. As her body relaxed, drowsiness washed over her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The dismantling of the Formation seemed to take much longer than expected.

When Qing woke up after a long, stretching sleep, the scene she saw was that same tiresome great hall of the palace.

Cui Liweng looked tired as he went back and forth between mountains, fields, and the palace. Well, the old man would naturally be tired if he kept moving around.

Qing, still being carried, started to feel embarrassed.

"Gramps, if you're tired, why don't you rest a bit?"

"Would a Master be tired from just staying up for a day? There is no need for useless worry."

"Or you could put me down. I can walk and run now, you know?"

"If you carelessly step somewhere out of curiosity, all the work we've done so far could be wasted. Just staying like this is more than enough help to us."

\textit{Is that so? Well, if you say so.}

With this justification, Qing proudly enjoyed her ride.

The process of dismantling the Formation was completely incomprehensible to a layman.

They would mutter unintelligible words, stand still, turn around, sometimes move backward or sideways, then stop at a point and kick the air.

Then an iron ball would pop out of thin air and roll on the ground.

This process was repeated endlessly.

And on top of that, she was hungry!

But she couldn't whine about being hungry when Cui Liweng's already sunken eye sockets were now even more hollow, casting shadows.

How could Qing possibly open her mouth to say she was hungry in front of that? Well, fun fact. She did anyway.

"I'm starving to death. What are we going to do about food?"

"What can we do? We will just have to starve."

"Ugh, this sucks. The bastards who set up this Formation should have their dicks cut off. Fight fair and square instead of laying out this kind of crap."

"Indeed. You are right. Those damn bastards."

Cui Liweng also gritted his teeth.

As she continued to starve like that, random thoughts came to mind.

\textit{If it's like this, wouldn't it be much faster if we woke up a few more people to help? Surely there must be more Formation experts among the Demonic Cult bastards.}

\textit{Wait a minute...}

\textit{Come to think of it, I knocked out a few people to see the location of the Heavenly Demon Spirit, didn't I?}

\textit{Haven't they woken up?}

\textit{Gramps regained his senses, but...}

As Qing was thinking about this, a voice suddenly caught her attention.

"Mom."

"Hoho, my son."

"Mom."

"Yes, mother is here. My son."

Qing turned towards the sound and frowned at the strange sight.

It was a beautiful woman with a vicious face.

While her face showed nothing but hatred, she was gently stroking the head of her grown son resting on her lap, speaking in a caring voice.

However, the son's face looked familiar.

"Ah! That motherfucker! Living the high life, huh?"

It was the Alleged Supreme, a bright smile plastered on his face.

"Gramps, put me down for a sec. I already decided I wouldn't let that fucker off easy."

"You need to say things that make sense. Can you not see how I am watching such a sight without being able to do anything? Why would I be going through all this trouble if I could do something about it?"

"Tch."

Qing clicked her tongue.

\textit{That fucker was claiming to be in the Natural Realm.}

\textit{But in the end, he's just trapped in the Formation, playing with his mommy.}

\textit{But this is also kinda unexpected.}

\textit{I thought the Alleged Supreme would take the highest seat and go on about being the emperor and all that crap.}

\textit{But his most desired illusion is just cuddling with his mommy?}

Qing made a disgusted face and asked.

"This is the Alleged Supreme's illusion, right? This is supposed to show the most desired illusion, yeah? Is this really what that good-for-nothing piece of shit Alleged Whatever wants?"

"Even the Supreme is pitiful if you think about it. He never got to be held by his mother even once, so such a regret manifests like this."

"What do you mean by that?"

"It is the karma that comes with Divine Blood. Tsk tsk."

A vessel carrying Divine Blood could not possibly be ordinary.

With strong bones and muscles, vast Qi and majestic blood, a clear Upper Dantian, and powerful Innate True Qi, they usually kidnapped the most suitable women from Zhongyuan to bear children with Divine Blood.

As such, it was rare for a mother to develop maternal instincts for a child she was forced to bear against her will.

The face she made when looking at the child she gave birth to was full of daggers, and when she opened her mouth, the sharp blades she spewed made her tongue truly worthy of possibly being called the Greatest Swordsman Under Heaven.

"Mom."

"Yes. My son. My lovely son."

"Mom."

"Yes. I love you too. My son."

The anger etched on the woman's face as she said these words was crystal clear.

Yet when hearing just her voice, it was so loving that it was rather chilling.

"Wait, but why does the mom's face look like that?"

"He has probably never seen any other expression in his life. He cannot even dream of a different expression. Even if it is in his imagination."

Qing was at a loss for words, her mouth just opening and closing.

The mother was glaring with a face full of venom, yet the Alleged Supreme still had a bright, happy expression.

Qing sighed deeply and swallowed her curses.

\textit{Seriously, fuck. Every single one of these Demonic Cult fuckers are the same. Not a single one of them is normal.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The dismantling of the Formation took place long after that.

It was enough time to be hungry, thirsty, nod off, and even get a headache to the point where she couldn't sleep anymore.

Qing had sunken eyes with an aching head.

Suddenly, Cui Liweng stopped walking and spoke.

"The Formation is disappearing."

"Ah. Seriously..."

'I thought I was going to die from exhaustion.' That was the unspoken latter part.

Ironically enough, this was what Qing thought. Let it be known once again that she had only been dozing off while being carried.

At this point, she could congratulate herself on achieving the feat of completely wearing down her 'triangle of conscience' into a perfect circle.

Like paper burning in dying embers, the world slowly started to burn away.

Ashes scattered everywhere, and beyond them, the dim tomb chamber gradually revealed itself.

Even though all the torches in the tomb had burned out, it wasn't completely dark, which must be why Banchi's technique of drawing light through small holes from outside the tomb was said to have reached the realm of Immortals.

The Demonic Cult members started to break free from their illusions.

Regretful sighs, occasional sobs of loss, or frustrated shouts echoed in the stone chamber.

Some even collapsed, sobbing and muttering names only they knew.

This was the reason why Zhi Shengzhu had mentioned how terrible this Formation was.

When caught in the illusion, one did not want to leave on their own, and even after the Formation was dismantled, they writhed in terrible feelings of loss. It was truly the essence of malice.

And because of this, Qing's opportunity had come.

"Heup!"

Qing jumped out of Cui Liweng's arms with a Thwop.

"Child?"

"Hehe, it's been a long time of humiliation..."

At the same time, Qing stomped on the ground hard.

It was the Anti-Gravity Step of the Yue Maiden Footwork.

A human shadow fell over the radiance of the Heavenly Demon Spirit, a triangular pyramid shining alone in the darkness.

Finally, Qing grasped the glowing triangular pyramid in her hand.

Qing took a deep breath, and then a loud voice filled the tomb chamber.

"Now! Attention! Everyone, can you see this!"

In that instant, everyone's gaze turned to Qing.

The dazed eyes, still affected by the aftermath of the broken illusions, soon discovered the Divine Relic in Qing's hand and changed to their respective reactions.

Some widened their eyes in shock, some just blinked in confusion. Others immediately knelt down and bowed their heads.

Among them, Qing made eye contact with Zhi Shengzhu, whose mouth was gaping, and winked at him.

Looking at Zhi Shengzhu's mouth shape, she could tell what he was saying even without hearing it.

'Damn it. Fucking bullshit.'

\textit{And the Alleged Supreme. Where the fuck is that bastard?}

\textit{Oh, the fuck? He still hasn't come to his senses?}

The Alleged Supreme was still standing blankly with a dazed look.

\textit{How can he be like this at the most important moment?}

\textit{Well, after I break the Heavenly Demon Spirit, he'll probably make some interesting expressions.}

Qing took another deep breath.

Now it was really the end. Once she left the tomb chamber and destroyed it, it would be goodbye to these annoying Demonic Cult bastards.

Just as Qing was about to deliver her lines...

Cui Liweng's shout cut her off.

"No! Child! Put it down right now! Quickly! If someone unqualified touches the Divine Relic…! That cannot happen!"

It was a desperate cry as if he was coughing up blood.

His widely opened eyes were shaking, and the emotion contained in them was clear fear. Fear? Terror?

Qing read fear in Cui Liweng's expression.

\textit{Why on earth?}

"I said put it down! Please! Are you trying to die twice in front of your father!"

Suddenly, her hand felt itchy.

Qing looked down at her hand blankly.

"Uh...?"

Qing made a dumbfounded sound.

After all, anyone would make a dumbfounded sound if they saw a self-illuminating triangular pyramid slowly seeping into their palm.