\chapter{Heavenly Demon Tomb (10)}

The Demonic Cult member exploded.

The cult members kneeling on both sides flinched as chunky liquid splattered on their cheeks.

Was it perhaps because it was the uncivilized ancient primitive China that pathologically hated cold water? The fluid was almost scalding hot even when soaking them thoroughly.

At this point, even the most devout (or ambitious) Divine Cult believers would start to have their faith shaken.

This was the Heavenly Demon Supreme who promised to bring eternal wealth and power through the liberation of Zhongyuan and the Divine Cult's rule over all under heaven.

Yet here she was, bestowing death by shooting Force beams with her finger.

The Demonic Cult members kneeling in the innermost circle began to slowly and stealthily back away, glancing around furtively.

The Heavenly Demon gritted her teeth and raised her foot.

It was said that the Demon God, the Master of the Demonic and destroyer of the world, set the world ablaze just by walking.

The world would turn to ashes and disappear, returning to the void where only darkness remained.

The Heavenly Demon's Reigning Step. The first step of devastation that crushes all Po and flesh by trampling the earth.

A magnificent energy capable of destroying stars gathered under the Heavenly Demon's foot.

Since the original owner's will was trying to protect this blasphemous old man, her vicious intention was to destroy the entire space.

It was a good attempt.

But just before the Heavenly Demon's foot touched the ground, the energy suddenly scattered, turning it into just an ordinary step.

If it hadn't been for that, Cui Liweng would have become a flat corpse like a squashed frog.

At that moment, there was a sudden mysterious movement, and the Heavenly Demon's foot slid back as if flowing like rivers and seas.

The opposite foot followed with the same technique, making it look like the Heavenly Demon was advancing majestically while actually retreating backwards\footnote{Moonwalk}.

This was a miracle that people couldn't believe even if they saw it with their own eyes.

It is the principle of the world that when a person walks, they push the ground away and their body moves forward.

The great Heavenly Demon had demonstrated the power to break even that obviousness.

"...?"

\textit{While it was an amazing technique, why? Why suddenly?}

The solemn silence that had fallen over the tomb chamber began to take on a slightly awkward and uncomfortable air.

It was like that eternal awkwardness when your friend leaves you alone with their friend whom you've just met.

In that uncomfortable atmosphere, only the Heavenly Demon kept moving backwards in a circle while facing forward.

'How dare mere humans try to understand the will of the great Demon God!'

The Demonic Cult members could only lament as their eyes trembled.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Riiip!

The duct tape that had patched up the wall was roughly torn off.

Having passed through the tape wall with her body, it naturally stuck all over him.

The Heavenly Demon, who had been flailing about as if chasing away bugs, finally threw away the ball of duct tape he had managed to clump together.

"Ah. You're here?"

Qing greeted the Heavenly Demon cheerfully.

She was holding a chicken leg in each hand.

"Sorry, but I can't give up the chicken legs. Of course, the wings and drumsticks are off-limits too, and the juicy part between the thigh and body is mine as well. The breast meat, well, it has its own chewing texture. So choose between the right or left chicken breast. Right? Left?"

Offering mere chicken breast, not even the tenderloin, was an insult worthy of getting slapped by a guest.

But it was an overly generous gesture for an uninvited guest who had broken through the wall and destroyed her security deposit.

The Heavenly Demon raised his voice in anger, stumbling over his words.

"What, what on earth is going on? Surely the root of your existence, your very Hun and Po, should have been damaged...!"

"Not telling. Well, the feeling of having your head explode was surprisingly okay. I'd say there was a certain sense of liberation."

Then she bit into the chicken leg heartily.

The Heavenly Demon frowned.

And as he raised his hand to point his finger...

"Stop! Stop that finger!"

Qing hurriedly shouted, spraying half-chewed chicken from her mouth.

"Hey now, don't mess with someone while they're eating. Even dogs bite when disturbed while eating, you know? I might just go more batshit crazy than dogs do. I was born human! I can't lose to those mongrels!"

The Heavenly Demon's mind went blank for a moment at this nonsense she had never heard before.

"...So, you are saying you shall be worse than a dog?"

"If you dance the Lustful Immortal Disrobing Dance in front of your believers, you'll regret it and think 'Ah fuck, I should've just quietly watched a mukbang instead', don't you think?"

This Heavenly Demon was also the one who had accepted the Bliss Palace.

After all, all Heavenly Demons were this man.

He knew what kind of dance the Lustful Immortal Disrobing Dance was.

If the Supreme of a religion were to strip and perform such a vulgar seduction, their reputation would be shattered forever.

(Though it was something Heavenly Demons in other worlds often did.)

The Heavenly Demon's mouth gaped in disbelief, and finally, with a deep sigh, he lowered his pointed finger.

"Fine. I will no longer touch your father. Is that enough now? Really, like father, like daughter. Clinging to such petty emotions. How can you, born as a daughter of the Divine Cult, interfere with our long-cherished wish of liberating Zhongyuan?"

This was a major misunderstanding on the Heavenly Demon's part.

In fact, it was an unavoidable misunderstanding.

The body the Heavenly Demon saw was a living corpse.

Naturally, he thought it had been created by Divine Cult members to receive the Heavenly Demon Spirit.

But when the old man jumped out to interfere, he thought it was because the old man who had breathed life into it and fed it for forty-nine days had become attached and saw it as his daughter.

And that the soul that had entered also took the old man as its father and gave him affection.

He had roughly drawn such a touching story in his mind.

However, it was a grand misfire.

"Huh? My father? Daughter of the Divine Cult? What are you yapping about?"

"I mean that insolent old man outside."

"Ah. Gramps? Gramps isn't my father!"

It was just pure, bright irreverence.

The Heavenly Demon asked seriously.

"What nonsense are you spouting? Clearly..."

"That old man's been a bit off lately. I saw it too, he's completely lost it. I don't have a hobby of pretending to be someone else, nor do I want to."

Qing had also seen Cui Liweng's passionate performance beyond the screen.

In fact, it was a completely unwelcome attitude.

She had only saved him because she had grown fond of him and pitied him, but if it weren't for this current situation, she would have immediately started some of that radioactive physical therapy to make him come to his senses.

"Then why on earth are you interfering?"

"Are you seriously asking because you don't know? Do you think I'd just stand by and watch as you all rush in while spouting nonsense about liberating Zhongyuan?"

"Haa. So it was merely your ignorance that was the reason."

"What? No, why do these people always..."

"Enough. You will understand once you see with your own eyes."

The Heavenly Demon cut off Qing's words and raised his hand.

Then the four walls of the one-room apartment fell backwards, revealing the outside scenery.

Hey now, why the fuck are you dismantling someone else's house as you please?

Qing grumbled, saying ‘Let's see how great the thing you're going to show me is', as she continued to tear into her chicken leg.

It was somewhere in Zhongyuan, full of people who were weak from hunger. Emaciated and ragged people were just sprawled about, with no sign of vitality to be found.

It was nothing short of a complete slum.

About ten men were walking around, checking on the fallen people. They spoke to them and waved their hands in front of their faces.

Finally, upon finding a corpse, they poked and prodded it, shook it, and when there was still no response, they picked it up with a faint smile.

As the men carried the corpses, at the end there was a huge cauldron-

"STOP! Halt right there! What are you doing while someone's eating? Even if you think this will make me yield, you're greatly mistaken. It's obvious this is just propaganda by you Demonic Cult bastards."

"I saw it myself. For over ten years, summers were cold and rain ceased, so crops couldn't grow. The animals were eaten long ago, and even after boiling tree bark to eat, even the trees withered away. It was an era where people just ate each other's corpses to survive."

"Eh? So this is for real?"

"However, not everyone went hungry. Look."

The world seemed to blur like a watercolor painting, then came into focus again, revealing a splendid palace.

It was a grand banquet with all sorts of delicacies spread out on a huge table large enough for twenty strong men to lie down on.

The man sitting at the head of the table, as well as everyone else at the table, had bulging bellies and multiple chins, their figures extremely ample.

"That man is the viceroy of the city we just saw. Instead of looking after his starving people, he squeezed them dry and held lavish feasts for every meal. The Daoist next to him is some Elder from Mount Hua, and everyone sitting here are either so-called Righteous Experts of the Orthodox Faction or the rich they protect with their swords."

"Is that Mount Hua the same Mount Hua?"

"Is it just Mount Hua? Shaolin Monks, Wudang Daoists, all those who call themselves the prestigious Nine Sects and One Union. They all cling to power and take the lead in exploitation."

\textit{Wait, Orthodox Wulin has such a dark past?}

Qing's eyes widened.

"The Orthodox Faction did not exist in that era. Originally, it was like that, so isn't it ridiculous how later on the same bastards divided themselves into Orthodox and Unorthodox Factions?"

For the Orthodox Faction to exist, there needed to be an Unorthodox Faction and a Demonic Path.

Without the 'Unorthodox Faction' and 'Demonic Path', there was no need to distinguish and gather only the more polite and courteous ones among the sword-wielding thugs.

If one had to classify, there were only two groups: the government and Wulin, and even then, it was an era where the government placed Wulin below them and treated them as unpaid volunteers to use for free.

"What the… This is just an old story, then."

"Keep watching. See how they oppressed those who were just crying out to be saved."

The scene unfolds.

An old man begging just to be saved from hunger, pleading for just a handful of grain, was met with only harsh beatings.

The old man who had been begging for even a bit of rice porridge to feed his sick child died like that, and his body was seized by pitiful, hungry ghouls who saw it not as a corpse, but as meat.

Unable to bear the sight, one martial artist stood up.

It was the man standing before Qing's eyes.

And so, raising a red flag shaped like the sacred fire of the Fire Worship Cult, he stood up, and soon the people's fervent-

"Wait. Can you not wave that red flag? Why a red flag of all things? Besides, this makes you the Yellow Turban Bandits, doesn't it?"

\textit{Wasn't this a Chinese game?}

\textit{Is it really okay to wave a red flag and say 'Let's build a people's nation together'?}

The reason she thought this way was because Qing hadn't played the game.

In the game, this was completely hidden and didn't even appear as a single line in the background.

"Yes, I admit it. Some cult members did call for the second coming of the Yellow Turbans. The results were similar too."

Spears and swords flew at the common people who had only risen up asking to be allowed to live.

The spears belonged to the army, and the swords to the martial artists.

And suddenly the scene shifted to the desperate escape of the survivors after the suppression.

They were a group that crossed mountains and rivers, traversed deserts with countless deaths, and finally reached a massive mountain range.

It was the beginning of the Heavenly Demon Divine Cult.

"And so, what remains is revenge. For me, and for all the descendants of the Divine Cult, there remains a revenge that must be carried out."

The man whose body was covered in scars, having lost all his family, friends, and revolutionary comrades, spoke.

All those countless scars were the graves of friends buried in his heart.

It was the grudge that burned even as he rejected death, calling himself the destroyer of the world.

Faced with this burning flame, Qing spoke.

"Motherfucker yapping some mad bullshit, huh."

"What?"

"The revenge is only left for you. The Demonic Cult bastards don't have any thoughts of revenge left at all."

Qing recalled her not-so-short life in the Demonic Cult.

They were a group of retards that didn't have a single speck of normalcy, but maybe that was natural given that the bitch known as their leader was like this.

"If you've aged and experienced the years in your life you should die gracefully. What's with this ugly desire to keep fighting until you win by changing bodies like some mental parasite?"

It was Qing's specialty, the Maw of Hell.

"Did you know? Someone who failed from the start is bound to keep failing no matter how many times they try the same method. When people fail, they should think about why they failed and try a different strategy next time, not 'This time the body was weak' or 'Last time we were a bit short on troops.' If you've already failed four times in a row, I'd be so embarrassed I'd just bite my tongue and fucking di-"

Thud.

It was the fatal weakness of the Maw of Hell.

Once the head flies off, it can no longer be unleashed.

The Heavenly Demon shouted with a red face.

"Very well, then. Let's see how you do. How long do you think a mere Peak Realm worm of a spirit like you can last if I keep killing you until you die? I shall make you regret moving that insolent mouth of yours!"