\chapter{Heavenly Demon Tomb (6)}

It was a truly stupefying scene.

An old man looking down at a young girl's corpse in his arms.

Next to him, a woman raising a deadly weapon high.

It was a scene where anyone would rush in to stop it immediately.

Moreover, here was one infamous Great Demonic Adept and one respected elder of the Daoist path.

With this explanation, even if countless blades rained down on Qing, she would have no right to complain.

However, the reality of the matter was that… the Daoist elder was Qing herself.

And this was precisely why people shouldn't have preconceptions.

Qing was in a serious dilemma, holding a divine weapon up high. Albeit, this 'divine weapon' was in the form of a Ten Thousand Year Cold Iron short staff.

\textit{Ah. About this. I'm not sure how much force to use.}

The old man was completely defenseless.

She couldn't gauge exactly how much force to use without cracking his skull.

\textit{Would a nuke be too strong?}

\textit{For now, let's start lightly, at the level of a brick breaker. Like TNT? Maybe?}

It was an infamous bomb generously packed with nine thousand catties of gunpowder.

As it was an item meant to blow up an entire city block, the gunpowder was very generous.

A bombardment of goodwill, deployed with the Imagery of that very brick breaker, fell in a straight line.

Thwack!

The sound of bone and metal colliding.

The old man's sparse hair and aged scalp did nothing to cushion the impact.

Originally, the crown of the head was called the Heavenly Spirit Lid and was the most important acupoint and vital point of the body.

As such, Cui Liweng's eyes rolled back when he took a direct hit while completely off guard.

He then immediately lost consciousness while still in a sitting position.

As his unconscious upper body tilted forward, he fell face-first onto the ground with a thud, sprawled out in a bowed position.

"Oops. Sorry, Gramps. I put a bit too much force into that. Hmm. But still, haven't you lived long enough for this to be considered a good death?"

\textit{It was supposed to be a legendary folk remedy to wake him up with pain, but it seems like I ended up knocking him out instead.}

This was why unauthorized physical therapy was dangerous.

That's when it happened.

Suddenly, the deafening sound of rain that had been filling her ears stopped abruptly.

Then the scenery of a dim stone chamber spread out in all directions.

It was a wide-open stone chamber with no obstructions.

Dozens of Demonic Cult Masters were walking around with dumb expressions, holding torches and forming several large circles facing outward.

Their gazes were fixed forward in a way that seemed rather inhuman.

Among them, only one person was looking around in all directions.

The little kiddo Zhi Shengzhu was turning his head back and forth between the inner and outer circles.

This was the scene of having escaped from the Formation.

Originally, when the owner of an illusion lost consciousness, it should have shown pitch-black darkness while the space was being filled with another illusion.

But the Great Tranquil Zen Art's principle of Right View pierced through the false void.

As it was a Buddhist teaching that respected others' perspectives, it still reflected others' illusions, but when there was no illusion, it simply shattered the falsehood.

It was a blind gap that even the unrivaled Banchi, the designer of this great Formation, hadn't thought of.

\textit{So this is what it looks like from the outside when someone is caught in a Formation.}

\textit{It's kind of... well... retarded.}

And then Qing saw the treasure.

In the very center of the tomb chamber, an object emitting a subtle five-colored radiance was practically screaming 'I'm a treasure!'

It was a self-illuminating triangular pyramid.

\textit{Self-illuminating, huh.}

\textit{And what do I call it… A sense of pressure?}

\textit{Or should I say, an intense presence?}

With just a glance, she had this spiritual intuition that this was the Heavenly Demon Spirit.

\textit{Wait, if that's the case, this is... an opportunity, right?}

The moment Qing took a step towards the center.

The world changed again.

It was the front of the gate of an unfamiliar house.

A Demonic Cult Master was repeatedly knocking on the gate with an excited expression, shouting.

"Honey, I'm home! I'm telling you, I'm home!"

-Darling? Is that you?

"Yes, it's me!"

-Darling!

Along with a desperate voice, light footsteps approached.

The Master's mouth opened, and his face flushed red with happiness and anticipation.

Finally, the sound of the gate's latch being undone.

And then, with a creak, the door began to open-

Thwack!

The Master collapsed and fell to the ground.

"What a cliché story."

Qing grumbled as she wiped Fushen-di.

The world collapsed, before returning back inside the Heavenly Demon Tomb.

Somehow, she was now standing in the outermost circle.

\textit{Earlier, I just wasted time looking around.}

\textit{This time, let's be quick.}

Qing stomped on the ground.

And the world changed.

Naked women were everywhere.

In the middle, there was one lone man.

Thwack!

Now there was no lone man anymore.

Back to the Heavenly Demon Tomb. Back to the outer circle.

After Qing knocked out seven Demonic Cult Masters and, for one case, just completely shattered his head for good measure, she came to a conclusion.

"Ah, shit. This isn't going to work."

If she killed them, she couldn't peek the outside, and if she just knocked them out, she could only escape the illusion for a moment.

But as soon as she took even one step, she'd return, so escape was impossible this way.

However, this alone was enough.

Because now she knew where the Heavenly Demon Spirit was.

Once the Formation disappeared, who could get their hands on the Heavenly Demon Spirit faster than Qing?

After escaping outside via a hostage situation and creating some distance, she'd destroy it and run away.

Master had said there weren't many in the world who could catch up to Qing's Qinggong, so she was confident in her escape.

So now, all that was left was for the Formation to be undone.

If she could just know in advance when the Formation would be undone and prepare for that moment, it would be as good as success.

For that, she just needed to stick close to the person undoing the Formation.

\textit{I'll find the kiddo and offer to help!}

Qing's cunning mind spun rapidly and came to a conclusion.

Qing took another step deeper into the Formation.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The plan was really good in theory.

But she didn't know where the kiddo was.

She was wandering through the illusions, thinking she might run into him if she just kept moving around.

In the courtyard of some bright, unfamiliar mansion… Or something like that…

A familiar voice picked a fight with Qing.

"You bitch, now you don't even see your father as your father? There is no one in this world who beats their own father. You are such a vicious brat."

It was Cui Liweng, who had regained consciousness.

Cui Liweng was a Master of the Unrestrained Realm.

He was too high of a Master to lose his life and head to the underworld from an attack that was merely heavy without any Qi infused into it.

Cui Liweng glared while rubbing his crown.

\textit{It seemed to hurt, at least.}

\textit{But 'father'?}

\textit{Did he really regain his senses?}

Qing, unsure, spoke bluntly.

"What? You still haven't come to your senses? Who's whose father? Get a grip. If you don't, I'll have to hit you again."

At that remark, Cui Liweng flinched.

He rubbed his eyes as if he had seen something wrong, then looked at Qing's face and sighed deeply.

"What's with you? Suddenly sighing after looking at someone's face? Do that and you'll get hit, you know?"

"To think there would be a young one who beats old people in this world. I knew you were a cruel bitch, but still..."

"This is why dementia is dangerous. How is it that respecting the elderly suddenly turns into attacking the elderly and all that? You know, that's why there's a saying about how there are no sages or saints in the face of a lunatic."

"...? Was there such a saying? Which Sage said that?"

"Ximen Qing."

Cui Liweng frowned.

But somehow… It kinda made sense to Cui Liweng, so he didn't bother to argue.

"I thought you were a cripple possessed by Inner Demons, but it seems you are actually a con artist who is a genius at deceiving others."

"At first, I really was a cripple, and as for the Inner Demons... Ah! So that's what Inner Demons were. Anyway, well. I overcame it well. Everyone was making such a fuss about how scary Inner Demons were, but it was no biggie after all."

To the Inner Demons who were listening in, they would feel chagrined.

Originally, they had enough skill to burn people from the inside and turn them into wrecks, but how could they have known that a legendary Formation would suddenly appear and interfere?

However, Cui Liweng roughly understood.

After being caught in the Formation himself, he realized that if there was a way to escape this illusion, it would be enough of a circumstance to overcome longing in an instant.

Thus, Cui Liweng's thoughts returned to the Formation.

"It seems a nasty Formation has been deployed, but how are you so unaffected?"

"I thought it was strange from the very beginning, you know? It was kinda obvious. So, it's not like I'm special. It's because those who fall for such trivial techniques are all weak. It's because they lack grit. Grit, I tell you."

This would be an unfair statement to the Formation as well.

In reality, Qing hadn't done anything well; it was just that the Buddhist purity of the Great Tranquil Zen Art kept poking at her dantian, trying to erase the falsehood.

Even then, she had forcefully suppressed it because she wanted to eat her hometown food, and only released it after she had eaten everything she wanted to eat.

On top of that, the Demonic Cult Masters would feel wronged too.

Come to think of it, Qing's greatest ability was the talent to make someone feel wronged every time she opened her mouth.

"Anyway, it's good I ran into you, Gramps. That kiddo said he'd remove? Push away? Well, whatever it is, he said he'd get rid of this Formation. He asked me to help, but since I didn't know anything anyway, I told him to just do it himself."

At that, Cui Liweng's expression brightened.

"That is welcome news. So, where is the Secret Pavilion Leader? I should lend a hand."

"The problem is, I don't know. I was hoping I'd find him if I just wandered around."

"Tsk. You always leave things so uncomfortably unfinished, don't you?"

"What's that supposed to mean? I kindly woke you up because I felt sorry for you getting rained on so pitifully. I don't need to hear this from an old man who hasn't even started, let alone finished anything."

"Ahem."

Seeing as he was just pretending to clear his throat, it seemed Cui Liweng had nothing to say.

"Well then, let's go."

"Alright. Let's go."

Cui Liweng replied like that.

And then he just stood there, looking at Qing.

"What are you doing? I said let's go?"

"Right. We should go."

"Then why aren't you going?"

"Ahem."

He pretended to cough uselessly again.

As Qing was watching, wondering why on earth the old man was acting like this, he quietly spoke in a small voice.

"I know you have been walking around inside the Formation all this time, but by any chance… Are your feet okay? Even if all this time, you were just pretending to be hurt… You should not strain muscles that have not been used for quite a while."

At that, Qing burst into laughter.

"If that's your wish, Gramps."

As Qing spread her arms, Cui Liweng carefully lifted her into his arms with a familiar attitude.

Even after her identity as a fake cripple had been exposed to the world, Qing shamelessly became a passenger again, following her Crutch through the main gate of the mansion.

Then suddenly, a thought occurred to her.

\textit{But whose illusion is this?}

\textit{The owner of the illusion seems to be pretty normal, huh? His mind isn't full of degeneracy.}

\textit{Well, whatever. Who cares who the owner is.}
