\chapter{Heavenly Demon Tomb (4)}

When Qing suddenly came to her senses, she was standing in the middle of an inn.

Qing naturally took a seat and called out.

"Excuse me! Server!"

"Yes, Young Lady. Coming!"

The server appeared, calling out politely.

"I'll have two servings of meat kimchi stew, with extra ham. Also, cola, cold please. Not hot."

"Young Lady, I apologize, but this inn operates with kiosks."

"Ah. I see."

Qing stood up from her seat with an embarrassed expression.

\textit{Seriously? These days everywhere has kiosks.}

\textit{But if that's the case, why did they pretend to take my order?}

Qing grumbled as she finished ordering and returned.

Then a dull pain surged from her lower abdomen.

Qing thought.

\textit{Be quiet for a bit. I need to be mindful of the situation.}

Qing forcefully suppressed the signal, resting her chin on the table and looking around.

By now, Qing had become accustomed to life in Zhongyuan, and she prided herself on being as savvy as an uncivilized local, especially when it came to inn culture.

Nevertheless, this inn was uniquely strange.

It was an inn where everything from the gray-colored floor and walls to even the tables and chairs were made of stone.

As if carved out of the inside of a rocky mountain.

On the other hand, it felt like being inside an unfinished building with no decorations or ornaments, as if the wallpapering hadn't been done.

\textit{Is this supposed to be one of those trendy aesthetic inns?}

\textit{But isn't this trend already outdated?}

\textit{But for something so outdated, the inn was packed with customers.}

\textit{It was almost full.}

\textit{Well. It's the owner's choice.}

\textit{As long as the inn has good rooms and tasty food.}

In the meantime, the food came out and was neatly placed on the table.

The long-awaited kimchi stew and white rice.

Qing took a spoonful of kimchi stew and put it in her mouth.

The spicy and rich broth, made by stewing well-aged kimchi, slid down her throat.

'My goodness!' Qing's eyes rolled back.

Then, she immediately launched into a battle-like meal.

Soaking the rice with the broth and mixing it well, then topping it with a piece of aged kimchi, a piece of tofu, and a piece of meat, she scooped up a heaping spoonful and stuffed her mouth full!

Then she cracked open a can of cold cola, feeling the fizzy sound on her tongue as she gulped it down!

Fireworks exploded in Qing's head.

\textit{Yes, this taste! This is exactly like the taste of home.}

\textit{I missed this so, so much.}

\textit{And I've been through so much to get here too...}

It was a taste that made her feel like crying; no, it actually did make her cry.

"What the, why am I..."

Qing wiped away the tears streaming down her face.

But tears were tears, and the meal was the meal.

Qing continued to shovel food into her mouth while crying unsightly, not stopping her hands.

Sob, sniff, munch munch, gulp. Sob, whimper, hiccup.

Crying and eating, crying and eating. A never ending loop of such actions. Basically, it was a complete mess.

Yet in contrast, her hand movements were very precise.

She sprinkled seaweed flakes and mixed it in, combining tofu, kimchi, meat, and ham in various combinations to devour the rice.

Originally, kimchi stew calls for two bowls of rice.

Qing battled with the food again over the second self-served bowl of rice.

"Whew. That was delicious. Hic."

Qing rubbed her swollen belly with puffy eyes.

Despite eating so much, her stomach was still flat.

And now she felt refreshed.

Whether it was because the food was delicious or because she had cried her heart out, she couldn't tell.

Regardless, she had overcome her Inner Demons while simultaneously having a meal and a good cries.

Qing leaned crookedly on her chair.

\textit{It's a bit disappointing. I wonder if there's anything else?}

Then she suddenly noticed a stone tablet that had appeared on the table.

Looking closer, she saw that the screen on the stone tablet displayed the inn's menu, grouped into large categories.

\textit{Ah. A tablet. Many places have these these days.}

\textit{But was this here originally?}

\textit{And why did I have to order from the kiosk?}

Qing skillfully operated the stone tablet.

Soon, a server appeared pushing a cart, setting down all sorts of desserts, filling the table with a parade of cakes.

Starting with tiramisu, there was a sugar-coated sparkling rare cheesecake, New York cheesecake on a crispy base, and ended with a deeply baked black Basque cheesecake; it was a full lineup of cheesecakes.

There was also chocolate chiffon and fondant au chocolat with a slightly cracked, hot interior oozing out. Strawberry fresh cream and an elegant milk cream without decorations, a crepe-style cake with layers of fresh dough and cream, and a mousse cake that could almost be classified as bread.

Eclairs with different colored toppings were neatly lined up in a row, along with maple syrup-soaked pancakes, opera cake, waffles, crème brûlée, custard with brownies, pies, tarts, macarons, cannoli, meringues, castella, and even tightly pressed croissants...

On top of that, Qing held a massive 31.01 fl oz Trenta size iced Americano in her hand, marking the birth of a dessert massacrer that no one in all of Wulin could stop.

Sweet, sweet, sweet, and more sweet.

After feeling refreshed from eating and crying her heart out, her mood soared with a lethal dose of sugar, resulting in the terrifying addiction symptom known in Wulin as a sugar high.

Then suddenly, a thought occurred to her.

\textit{Since when did I like sweet things this much?}

Qing's hand stopped.

The apple marmalade from the pie she was about to bite into dripped down.

Before the start of this journey into Wulin, she didn't particularly avoid sweet things.

But she didn't go out of her way to eat them either.

This sweet tooth was a preference of her current body.

If that's the case, isn't this somewhat dangerous?

"Ah, shit. And here I was thinking I'd enjoy it a bit more."

Qing tossed aside what she was holding.

At the same time, she released the force constricting her dantian.

The True Qi of the Great Tranquil Zen Art, which had been constantly poking at her lower abdomen and causing a fuss, was released.

That serene yet clear and bright True Qi flowed up her spine towards her brain.

The eight practices of Buddhism were called the Noble Eightfold Path.

And among them, the first was Right View, which meant seeing the world in a correct manner.

Thus, Qing recognized the illusion.

What she was seeing, hearing, and feeling right now was not reality.

Qing smacked her lips.

\textit{Well, at least I got to eat kimchi stew to my heart's content.}

\textit{I should be able to endure for another three years now.}

\textit{When I get back to the Divine Maiden Sect, I should try making kimchi.}

\textit{Isn't it just soaking cabbage in salt water, then smearing it with minced green onions, garlic, onions, and peppers before burying it?}

\textit{If it doesn't work out, I can always come back here, I guess.}

\textit{But, what on earth is going on here?}

Qing asked a very, very belated question.

From the start, she had easily noticed something was off because of the Great Tranquil Zen Art's True Qi acting up.

She had forcefully suppressed it, wanting to satisfy her gluttony first.

And having thoroughly enjoyed herself, it had been a genuinely happy moment in a long time.

\textit{What is this? Some kind of mental hallucination magic?}

\textit{Do such things exist in wuxia too?}

\textit{I mean, I've seen Master shoot fire from her hands and fly around on swords and all that.}

\textit{And now apparently, there's even hallucination magic on top of that.}

\textit{Then what's the difference between wuxia and Harry Potter?}

\textit{These guys can fly around, shoot fire, and show hallucinations. And if that's enough, there are even these Demonic Adepts as public enemies.}

\textit{Is it just called wuxia if there are ching chongs in it?}

It was a blasphemous thought that would make the eight billion nine hundred and three million wuxia enthusiasts, thus representing the greatest creation in human history, foam at the mouth and roar in anger.

Qing had such thoughts as she walked out of the inn with clicking steps.

And as she stepped outside the inn, the scenery changed again.

Inside a palace hall with a high ceiling.

It was a sight of countless thrones, each occupied by a single person.

Thinking about the familiar faces, she realized they were the elite Demonic Adepts of the Demonic Cult.

Some Demonic Adepts were sitting on high thrones, receiving fruit from beauties, while others were also sitting on high thrones, receiving bows from silk-clad officials, and yet others were also, also sitting on high thrones...

Qing frowned hard.

"What the hell? Why do all these motherfuckers look like they're meant to be kings? Isn't there anything more original?"

Well, that was because the dream of most capable individuals in the Demonic Cult was to become a king.

After unifying Zhongyuan, they wanted to receive a royal title, rule over a city, and live happily ever after.

Qing pulled out Fushen-di.

She intended to help them snap the fuck out of it, seeing as they couldn't seem to get their shit together.

Basically, she was going to send them straight to Ascension, to that far, far away place high in the sky where Immortals supposedly dwelled in Sukhavati, also known as the Pure Land of Bliss.

Just as Qing was approaching the nearest throne with an ominous smile...

"Please stop."

A youthful voice stopped Qing in her tracks.

Qing turned her head.

The ominous smile remained.

"Well, well. If it isn't Shengzu? How nice to see you like this? I was just thinking I wanted to see our Shengzu's face. And maybe take a look at what's inside that face too."

Zhi Shengzhu looked alternately at Qing's smile and Fushen-di, backing away hesitantly.

Then he hurriedly spoke.

"If you kill me, you shall be trapped in this Formation forever. Are you okay with that?"

"Huh? What? Formation?"

"The Phantasmal Maze of No Return Formation. It is an evil Formation of the Blood Sect, a branch of the former Blood Cult. You must have at least heard the name."

"Huh? What? Formation?"

Qing asked again.

Zhi Shengzhu looked at Qing with trembling eyes.

His pupils shook with amazement at how someone could be this ignorant.

"Did I need to start explaining from there?"

"Yeah. So, what's a Formation?"

A Formation was a type of technique that utilized the Qi of nature.

It was also a highly advanced skill that required knowledge of the geography of heaven and earth, thus where water veins and spirit veins flow, as well as the ability to read the results that appear when twisting these flows.

Thus, humans who entered a deployed Formation would see illusions, hear hallucinations, have their five senses all fucked up, and be unable to wake up as they failed to recognize the unreality.

"Ah. So this mess is because of a Formation?"

"The Phantasmal Maze of No Return Formation is a terrible Absolute Formation that shows the illusions that humans most desire or long for in their lives."

"Why is that terrible?"

Qing asked back in confusion.

Hadn't she just eaten everything she wanted to eat and even completely cured her Inner Demons?

"Because it makes people not want to escape from the Formation. The illusion of eating is not actually eating, and being awake without sleeping becomes a sweet poison that takes away human life."

Qing tilted her head.

\textit{It wasn't that bad, was it?}

As usual, Qing didn't just think to herself.

"Hmm... Is it really that serious?"

"Damn bullshit. Ah, I apologize."

Zhi Shengzhu immediately apologized.

For some reason, he couldn't help himself.

He couldn't understand why that single phrase could grate on his nerves so much.

"It is an Absolute Formation where one's Imagery actually reveals itself and becomes visible to others. It seems to be based on the principle of completely melting the Five Elements into the One Hundred and Eight Qi Gates, but to find the Life Gate among them, you first need to find the basic Eight Trigrams Axis's Spirit Four Gates and Seven Section Gates..."

"Hey."

Qing cut off Zhi Shengzhu's chatter.

It was all meaningless yapping she couldn't understand anyway.

This was the problem with smart people.

They think everyone else is as smart as they are.

This was also why Qing had evaluated Xue Ganom as the neighborhood's greatest intellect.

At least Xue Ganom's explanations were always easy to understand.

A smart guy talking about things only he understands?

Qing already had an effective method in hand for such situations.

The most effective means of communication when it came to these professor types - the Fushen-di.

Qing raised the Fushen-di and spoke.

"Do you want to keep using difficult words?"

"...There are five hundred and forty ways to escape the Formation, but except for five of them, they are all traps. So it is practically impossible to find the way out."

Zhi Shengzhu immediately changed his manner of speech.

Knowledge might be in high places of glory and esteem, but unfortunately the Fushen-di was right in front of him.

"You should have said that from the start."

Qing nodded.

"So, what do I need to do now?"

"All Formations have a central pillar, that is... Yes. A cornerstone. Ah, a cornerstone is-"

"I know what a cornerstone is, you know."

"That is impressive."

"I'm always impressive. There's never been a time when I wasn't impressive."

"..."

After a moment of silence, Zhi Shengzhu spoke again.

"We need to remove those cornerstones in the correct order and place to dismantle the Formation. So you just need to move the objects as I tell you."

Then Qing replied.

"Me? Why should I?"
