\chapter{Heavenly Demon Tomb (2)}

The salty taste that scrapes the tongue, the sweet taste that makes your mouth pucker.

The spicy kick from the harmonious blend of green chili peppers, garlic, green onions, and onions.

And the savory umami created by dumping in MSG, arrogantly named the foundation of flavor!\footnote{Uncle Roger approve!}

The sweet, salty, spicy, and hearty flavors of Korean cuisine were created by these four great elements.

But you see.

Salt is not cheap.

Sugar is very expensive.

Chili peppers, a spice from India that was a rather hot topic, was unfortunately unfamiliar outside of Sichuan.

MSG? Umami?

This was a taste of dedication that could only be obtained by simmering the bones of a beast for an excruciatingly long time until the bones turned mushy and the marrow completely melted!

It was humanity's unique culinary art that couldn't be dismissed as mere white powder.

So though Qing's homesickness was represented by kimchi stew…

In reality, it was a longing for Korean cuisine that encompassed the four great elements of taste.

It was a thirst that couldn't be quenched by pseudo-Korean food.

The soul of the Korean people, fried chicken, existed in Zhongyuan too.

To begin with, there was no civilization as rich in oil as Zhongyuan, where even rural peasants developed fried dishes.

Samgyeopsal\footnote{Grilled pork belly}?

Pork was the most common ingredient in Zhongyuan.

Noodles?

The Zhongyuan was the starting point for all noodle dishes in the world, the origin without which noodles would not exist in this world.

So the fact that Qing had succumbed to her Inner Demons due to lovesickness at this point in time rather than earlier could actually be considered praiseworthy. It was a miracle she lasted this long.

After all, it was merely an imaginary ideal food that her soul desperately sought.

Qing's expression was indescribably sorrowful.

For reference, there is a beauty that transcends time and worlds in the expression of a woman longing for something desperately.

This is because longing originates from a desire for lost beauty.

And the people of Zhongyuan were a race that found such desperate longing more beautiful than any other people in the world.

Basically, they were a group of fucking perverts whose sexual desire exploded at the sight of a slightly frowning expression, their eyes rolling back in veritable ecstasy.

Xi Shi, the most beautiful woman in Zhongyuan, was merely frowning because she had difficulty breathing due to her chronic pneumothorax, but everyone in the world thought Xi Shi was longing for something.

As such, that was why even the elites of the Demonic Cult were on the verge of falling lovesick.

Because by now, Qing had become a beauty who could hold her head high anywhere she went.

Though, of course, that beauty of hers would shatter spectacularly the moment she walked, ate, or spoke.

However, Qing was not in her right mind.

The heart-wrenching sorrow emanating from her longing pierced the hearts of the Demonic Cult Masters.

'Hey. Today I finally realized what face my ideal type has.'

'You too, Elder Brother? I was just thinking the same.'

'Stop stealing glances at my sister-in-law. Her face will wear out from all the stares you're giving.'

'Sister-in-law my ass, shouldn't you get through Father-in-law first?'

However, there was a Great Demonic Adept escorting the beauty.

If it weren't for the Purple Lightning Demonic Warlord, countless evil handsha- No, marriage proposals would have already flown towards Qing.

But Cui Liweng was an Unrestrained Realm Demonic Human who exuded Purple Lightning Force with his mere approach.

He had the ability to turn people into charcoal if he was in a bad mood, and the Demonic Cult was a group that didn't punish unauthorized charcoal production.

So everyone pretended not to look while still stealing glances at Qing's sorrowful expression as she was held in the Purple Lightning Demonic Warlord's arms.

The Purple Lightning Demonic Warlord kept sweeping the surroundings with cold eyes to dispel the gazes, but it was uncontrollable as people kept glancing from here and there.

Cui Liweng clicked his tongue and spoke.

"Child, why are you so listless? Even a limp puppy would be more lively than you."

"Kimchi stew… I want to eat kimchi stew…"

"Kimchi stew? What a strange name I have never heard before. Wait, you want to eat? Are you throwing this tantrum just because you want to eat some food?"

"Just food… What do you mean just food… You're so mean…"

Cui Liweng's eyebrows twitched.

With her usual temperament, she would have immediately lashed out, asking why he was belittling food without understanding her feelings.

She wasn't the type to weakly say 'You're so mean' and let such a comment pass by, like a squid taking its last breath.

It was then that Cui Liweng realized something was seriously wrong.

He had said 'just food', but this old man who had lived a long life didn't think she was merely throwing a fit over food.

This child, surrounded by nothing but Demonic Adepts with no one to care for, was missing home, and that manifested as a craving for food.

\textit{How much must she be longing for it that she was like this?}

However, Cui Liweng couldn't be proud either.

He had promised to send her back.

He would keep that promise, but he could clearly envision the scene of a child who had already learned Demonic Arts losing her place to return to.

So instead, he asked a different question.

"Alright, alright. I hear you. Since it is 'just food', what reason is there that we cannot make it? Tell me a bit more about it."

A glimmer of light returned to Qing's eyes.

"Really? Kimchi stew is a soup made with kimchi."

"And what is kimchi?"

"Oh. It's like a pickled vegetable made red with chili peppers? But it's not just pickled on the outside, it needs to be fermented."

"When you go back-"

"But I can't go back…"

Qing slumped again.

Cui Liweng was at a loss.

\textit{It seemed to be some kind of local cuisine.}

\textit{A red fermented pickled vegetable?}

\textit{It was very strange, but the problem was that it couldn't be made just by having the ingredients.}

Cui Liweng sighed, not knowing what to do.

And one of the Demonic Cult Masters who had their heart stolen by the pitiful beauty eavesdropped on the conversation using their Aural Technique that had reached the Grand Star.

Aural Technique referred to the art of concentrating Inner Qi to pick out and listen to a single sound.

Through this, Masters could hear distant sounds or filter out various noises to pick out only the desired conversation.

In other words, its original purpose was for eavesdropping, a technique for listening in on others' conversations like this.

Anyway, the eavesdropping was successful, so it seemed it was indeed worth reaching the Grand Star for.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

\textit{Ah. I want to eat something spicy and hot.}

Qing picked at her food, unable to rouse her appetite.

But in fact, she only appeared to be picking at her food in Cui Liweng's eyes.

It was only after her gluttony died that a Ximen Surin Classic shone through. The art of rote learning through the medium of nuclear attacks. The education of repetition.

Only after her instincts died did the habits engraved in her body, the beautiful behavior patterns engraved with such nuclear energy, pop out.

So to people who didn't know Qing's true nature, it looked like the perfect meal of a flawless beauty.

\textit{This is sweet. This is salty.}

\textit{There's no rice, and everything is so greasy that I wanna kill myself.}

Qing finally put down her chopsticks.

It was a major event where Qing refused food.

That's when it happened.

"Young Lady. Please have this."

"…?"

Qing turned her head dazedly.

As clear sorrow seeped through her languidness, the heart of the Master offering the bowl pounded.

"I heard this was a local soup. You didn't seem to like the food, so I brought this."

The other Masters who saw this scene thought, 'Oh my goodness!'

'Damn it, so there was a method like that!'

'To catch a horse, shoot the general, right? Wait, is that the correct saying?'

'Anyway, he who captures the stomach rules the woman's heart!'

To be fair, in Chinese-style romance, men were forced to be more devoted than any other race in the world.

The thing about Chinese-style romance was that (Omitted, will speak about it next time if there's chance)

As such, Qing would experience this firsthand anytime once she went out to Zhongyuan, seeing as she was already a beauty.

Qing looked at the soup.

\textit{It looks all clear and bland… It doesn't seem right at all.}

\textit{But you never know…}

Qing brought a spoonful of soup to her lips delicately.

It was salty, sour, and greasy.

\textit{Sourness in a soup for a meal? That ain't it, Chief. Really.}

\textit{How can the world be like this? Is it this hard to just have a bowl of spicy soup?}

Normally she would have thrown a fit, but due to her Inner Demons, she just quietly despaired and put down her spoon.

Besides, kimchi stew was also, in fact, a spicy and sour soup.

And from that moment on.

All sorts of soups appeared on the table at every meal for Qing.

At first, Cui Liweng glared, but seeing her take a spoonful each time, which honestly added up quite a bit, he reluctantly withdrew his killing intent as if to allow it.

Nevertheless, it was such a great tragedy that Qing never got to taste spicy soup in the end.

Xue Ganom should have seen this scene.

Then he would have imparted the realization that if she had just kept her mouth shut and pretended to be upset, she would have been treated well anywhere.

But Xue Ganom was gone now…

And so, day by day, the flock of Demonic Cult members was getting closer to the Heavenly Demon Tomb.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Another week passed like that.

The villains of the Demonic Cult, disguised as merchants, set foot in Gansu.

Gansu Province was shaped like a snake's head stretching long and far. The reason for the formation of this strangely narrow and long capital city was simple.

What else could have been done when there were such high mountain ranges both above and below?

As such, this was the only flat path that went beyond Xinjiang, squashed between the upper and lower barriers, thus heading towards the Western Regions.

So many merchants passed through this route, and because they all walked piled with silk, this road's nickname became the Silk Road.

The sight of merchants flocking to the Silk Road was all too common, so the Demonic Cult's invasion force, disguised as merchants, didn't arouse any suspicion.

Then suddenly, the merchant group sharply turned south, reaching the famous Qicaishan, also known as the Rainbow Mountain, of Zhangye.

For reference, Qicaishan's literal definition is 'Seven Colored Mountains', hence its name because the mountains had seven colors.

Qing, who had been in a listless state, saw this sight.

\textit{Ah. I think I've seen this back when I was in actual civilization...}

She was talking about the famous Zhangdan Danha, internationally known as the Zhangye Danxia Geopark.

It was an incredibly mystical landscape where the barren land, void of vegetation, drew waves of seven colors.

\textit{It's interesting, but...}

\textit{It's just colored land.}

The mentally unstable Qing abruptly concluded her appreciation. She did not have the energy to give a flying shit.

If Qing had been well-versed in the geography of Zhongyuan, she might have guessed the location of the Heavenly Demon Tomb at this point and slapped her knee in realization.

Following the mountain range south from Qicaishan, one would reach the Pingshan Lake Grand Canyon.

Vertical cliffs stood as walls, and the winding canyon between them was a natural maze in itself.

Considering that, where else under the heavens could the budding seed of such a huge calamity be hidden if not in Pingshan Lake!

…was what she would, or rather should, say. But unfortunately, Qing's knowledge of geography fell far too short to marvel at that.
