\chapter{Heavenly Demon Tomb (11)}

The image of the Heavenly Demon continuously advancing backwards while drawing a circle was an amazing sight no matter how many times one saw it. Just watching was enough for anyone to be fascinated.

Moreover, the circle drawn was perfect without any distortion, and all movements were exactly the same without even a millimeter of error, not showing even a hint of humanity.

However, separate from that, as time passed, questions about what on earth was happening began to arise.

However, how could the Demonic Cult members possibly know the inside story?

That even with two minds, the mind manifested externally was in a state of mindlessness, and that it was just repeating the same motion in response to the command 'dance' as an expression of emotion.

Zhi Shengzu felt extremely awkward about the blasphemous gazes that occasionally reached him, those unfaithful glances that dared to ignore the Heavenly Demon Supreme and look away.

As the Secret Pavilion Leader and Demonic Brain, he knew nothing.

He had no choice but to pretend not to notice the gazes that kept prodding him to say something, anything.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Heavenly Demon had already experienced subduing the same number of minds while changing bodies dozens of times.

This meant that when it came to the mind, he was the unparalleled authority in the entire world, including not just Zhongyuan but also the borderlands.

(To people of Zhongyuan, everything outside the Zhongyuan was considered the borderlands.)

Compared to that, Qing's skill was just at the level of setting up a one-room apartment and making fried chicken.

There was nothing exceptional about it; it was just an average level. Even the owners of previous bodies had all done this much.

It was nothing more than an instinctive defense mechanism where people visualize the most familiar place to protect themselves after losing their body.

As such, the Heavenly Demon couldn't understand.

He couldn't comprehend where the strange immortality of Qing's mental body came from.

He could only guess that since the scenery created by Qing's mental body was unfamiliar even in the Heavenly Demon's long life, she might be a person from the very edge of the borderlands or beyond. He thought perhaps the barbarians there had developed techniques for handling the mind.

"When someone speaks, you should at least pretend to listen."

Thud. Plop.

"Shit. Let me run my mouth for a bit too."

Thud. Plop.

"Aren't you getting sick of it yet? At this point, you should know that it's no u-"

"What could it possibly be... This ability to learn..."

"Oooooh, loser."

"They say if you are lacking in the head, your body suffers."

Plop, plop, plop.

Countless headless corpses littered the ground.

"Come on. Didn't I already tell you that if something doesn't work no matter how many times you try, you should change your method? Like this."

This time, Qing's figure couldn't be seen.

The Heavenly Demon looked around nervously, searching for the owner of the Maw of Hell.

"Come to think of it, isn't Divine Blood just a continuation of all your children? Then what, you're both father and child? So, would your wife also soon become your mother? When you get bored preparing for war, do you call your mother and fuck her once in a while for old times' sake?"

"How, how dare you spout such nonsense!"

"What do you think when you look at your children? 'This is a body I'll possess later, so I should treat it preciously'? It must at least be convenient not having to teach them morals. You don't need to give affection to children who'll die by your hand anyway, right?"

Qing was employing an incredibly vile tactic of just running her mouth while hiding among the corpses.

Despite being covered in blood and pretending to be a corpse, her mouth was very much alive.

But bodies with the same clothes and shape had practically formed a layer on the ground.

Finding one with a head among them was like playing a hellish game of Spot The Difference.

The Heavenly Demon, who had never even played a spot-the-difference game at a 7-year-old level, let alone a hellish one, finally burst out in frustration.

"You wench, what do you know! Those detestable Zhongyuan bastards! Look at their descendants! Do they dare not know that all their prosperity is built on the evil deeds of their ancestors!"

"You want them to atone for their ancestors' sins? That's a bit..."

"Is it not only natural!? They inherit their parents' wealth and connections and enjoy them as if they are rightfully theirs! Are they going to just leave out the ugly sins and history of exploitation!"

"Eh...?"

Qing hesitated.

\textit{Doesn't that... kinda make sense?}

"Look at those so-called prestigious Orthodox sects! They are born and immediately have their meridians opened, consume Elixirs, and train in precious martial arts, so even the dullest person in the world will reach the Transcendent Realm before they die! The wealth and glory obtained through exploitation have created the eternal rulers of Zhongyuan! Yet they claim to be without sin!"

"They do... have sin, don't they?"

Qing couldn't completely deny that.

After all, there was a certain island nation that immediately came to mind, and anywhere you pointed on the continent next to it was the same.

Of course, that didn't mean she had nothing to say.

"Even if that's true, you don't particularly have the right to punish them, do you?"

"No! If there is even one person in the world who has the right! It is me! I, who clearly witnessed the sins of the past and lost everything to those atrocities!"

"This is kinda strange, no? Is this something a mere evil spirit specializing in losing streaks, who just steals other people's bodies and has never won even once, should be saying? By the way, I'm asking because I really don't know."

"What human in this world could transcend death! This is the will of the Heavenly God Ahura Mazda, bestowed upon me to right the wrongs of the world! This is the will of the heavens, I tell you!"

Qing snorted.

\textit{What is this bullshit about heaven's will creating some kind of superman to punish the world's evildoers?}

\textit{Why not just say that Ahura Mazda or whatever god spoke to him directly?}

"Huh? The heavens created you to deliver divine punishment? Instead of doing it directly? The fuck? I seriously-"

\hspace{2em}\textbf{-cannot listen to your bullshit anymore.}

Suddenly, Qing's voice thundered from the sky.

It was a sound that filled the world like thunder.

The Heavenly Demon looked up.

Above the sky, a huge square frame could be seen.

It was a window attached to the sky, showing an even higher world.

Beyond it, a giant face appeared, Qing's gaze looking down on the earth without hiding her disdain.

"W-What is this..."

\hspace{2em}\textbf{-What else? It means you're in the palm of the Buddha.}

The world shattered into sharp fragments and poured down.

The countless corpses and sticky blood were now gone, and the revealed earth showed its true form as a palm made of white, fine skin.

Qing looked down at the Heavenly Demon on her palm.

The Heavenly Demon screamed in fury.

"Impossible! How can the consciousness of a mere thing like you be greater than mine! Someone who is merely in the pitiful Peak Realm!"

\hspace{2em}\textbf{-I don't know either. It was like this after I died once.}

Qing smiled like a god in her enormous form.

\hspace{2em}\textbf{-So, try stating your claim again. What did you say? The what of the heavens?}

The Heavenly Demon gritted his teeth.

"If not the heavens, who else could revive the dead! It is me! I have received the Mandate of Heaven!"

Qing answered with a laugh.

\hspace{2em}\textbf{-Well. If you say so, then I guess that's how it is. Then you go ahead and be the will of the heavens. But you know what? Where is Heaven's will right now?}

"That will is in me! I am Heaven's will!"

And that very Mandate of Heaven was in Qing's hand.

Flesh-colored pillars, mountains, rose up from the ground where the Heavenly Demon stood.

It was because Qing had clenched her fist.

Just a single bug on her palm.

It was so insignificant that when lightly crushed, even the remaining blood was just a few drops, not enough to flow out.

Finally left alone, Qing giggled.

"Too bad. The Mandate of Heaven ends here. Heaven wasn't much after all, huh."

At the same time, Qing looked at the transparent window.

It was a message that had been annoyingly flashing in front of her since the moment she absorbed the Heavenly Demon Spirit.

\begin{quote}
Status Window
\medskip

[Currently automatically progressing in the form of the Heavenly Demon.]

[Cancellation of Heavenly Demon's form is possible.]

[Do you wish to cancel? Yes/No]

[*If you select No, your journey will end and lead to the Heavenly Demon Divine Cult Ending.]
\end{quote}

Soon, the 'Yes' text flashed a few times, and the Status Window faded away.

Qing thought.

\textit{Was this prepared as a hidden ending in the original game too, with the body being stolen?}

She didn't know why cancellation was possible.

Maybe they made it possible to choose so people wouldn't get angry if suddenly presented with a Game Over.

Or maybe she had already met certain conditions that allowed for immediate cancellation.

For example, it could be due to the Heavenly Slaughtering Star, or the Blood Poison might have considered it an intoxication that could be canceled.

Or it could be thanks to the martial arts she had learned.

The Great Tranquil Zen Art of Buddhism might have established the Buddhist law of self. The Yue Maiden Cultivation Technique of Jiutian Xuannü, who was in charge of the boundary between the Nine Thousand Worlds above and below, might have exerted its power.

However, Qing didn't know anyway.

She wasn't particularly curious about the reason either.

Ximen Surin might have thought differently.

The Fire Worship Cult worshipped fire, which meant the holy fire of Ahura Mazda, the Sun God.

The God of Destruction, Angra Mainyu, represented the pitch-black darkness, the night that humans primordially feared.

The sun illuminates the night, so Angra Mainyu was just a lower god who couldn't dare to oppose the Sun God and cowered before him.

And the Heart Cleansing Mirror of Zhu Xiang was the Imagery of the Flame Emperor.

The Flame Emperor was the Sun God worshipped by the Chinese people.

So couldn't it be said that the outcome was decided from the start?

Regardless, Qing didn't have that level of knowledge.

However, isn't just the fact of knowing that something is possible to do still important to know?

"Give me back my body, you punk."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Heavenly Demon, who had been showcasing a dance ahead of its time, finally stopped moving and stood in place.

And as she walked step by step, she was once again in front of the old man Cui Liweng.

Cui Liweng's blank eyes wandered around her feet.

That's when it happened.

Suddenly, the Heavenly Demon's foot moved, aiming for the lower abdomen of the Supreme, who Cui Liweng had subdued and pinned to the ground.

THWACK!!!

"ARGH!"

The Supreme's mind snapped back to clarity from the pain of his dantian being shattered. This was the essence of medicine that could revive even a dead mind - physical therapy.

"You fucking bastard. I told you I wouldn't let you off easy, didn't I? Hm? Or wait. Maybe I didn't say it out loud?"

Qing continued with a vile smile.

"What did you say again? Natural Realm this, setting your mind to that? Yap yap yap? Now that your dantian is shattered too, how does it feel to become a natural person instead of Natural Realm, you motherfucker?"

Only then did Cui Liweng also come to his senses.

Physical therapy was originally highly effective not only for the patient but also for potential patients watching.

"Child, Qing, is that you, Qing?"

"Hm? Gramps? Have you come back to your senses again? Stop getting confused about daughters or whatever. Why do you keep messing with other people's family trees? Hmm. I want to eat bossam and jokbal."

\textit{I should have ordered it when I could earlier during that imaginary space.}

\textit{Why do I never think of these things at the right time?}

Qing regretted it, but it was just a slight disappointment.

Because not only was she no longer fixated on hometown food, but jokbal and bossam existed in Zhongyuan too.

There wasn't a culture of enjoying the original jokbal hongshao zhu, the original bossam dongpo rou, and the original bibim noodles banmian all at the same time, though.

But still, isn't that up to the person ordering?

\textit{I just need to add some clear rice wine to that. Then, bang boom pow! Based as fuck. Kyaaaa that's the shit.}

"You!"

Right as Qing was in the middle of swallowing her saliva while spreading her wings of culinary imagination…

A young, ill-mannered voice rang out sharply.

Qing turned her head.

With a triumphant smile.

"Ah. Kiddo. Right. You were here too, yeah?"
