\chapter{Heavenly Demon Tomb (12)}

"The Heavenly Demon Supreme… What has happened to the Heavenly Demon Supreme?"

"After coming out to the world after so long, he got tired and is resting."

"Is that really true!?"

"I don't lie with my own mouth."

Qing said proudly, puffing out her chest.

In reality, Qing was only honest with her mouth.

After all, deception and lies were not the same thing.

She had never explicitly denied that she was the culprit behind Heavenly Demon Supreme's current state.

Zhi Shengzu didn't hide his suspicious gaze.

From the heads of assassins to pretending to be a cripple (which to Zhi Shengzu just looked like an actual cripple), she was a woman who couldn't be trusted at all.

Moreover, when the Heavenly Demon Supreme was acting strangely, he kept cursing at a wench, so there was no need to think deeply about who the culprit was.

"Do you have any proof?"

"Hoho. Your gaze is very nasty. Do you dare doubt Ximen Qing, who has received the Heavenly Demon Supreme, the living incarnation of Ahuda Mazda?"

"It's Ahura Mazda."

"Potato, potahto. Well, proof? Right. Just a moment. Hmm. Yes. Okay. I'll do that."

Qing muttered like that while nodding her head.

It looked as if she was talking to someone inside her.

Just as Zhi Shengzu was starting to get confused...

"Now. Listen. These are the words of your Supreme."

As Qing opened her palm, the Heavenly Demon Spirit popped out and emitted a somewhat lackluster radiance.

The cult members, who had been slouching while watching carefully, immediately straightened up and focused their attention.

"The Supreme speaks!"

Qing clenched her fist tightly.

-AAAARGH!

A desperate scream echoed from the Heavenly Demon Spirit.

It was a scream in the Heavenly Demon Supreme's own voice, no less.

The pain of having one's soul wrung out is the worst thing that cannot be described in worldly expressions.

If a living person experienced it, they would die instantly from the shock.

But those already dead have lost the right to escape through death.

Of course, Qing didn't know this pain as she hadn't experienced it.

However, if even the Heavenly Demon was throwing away all dignity and reputation to scream so desperately, it must be no ordinary pain.

\textit{Serves him right.}

When Qing opened her hand, what remained was a triangular pyramid cracking and crumbling with fragments flying off.

The mystical radiance was gone, flickering feebly like a sad firefly.

Qing spoke with a triumphant smile.

"Since you ignorant lot can't understand the Supreme's voice, I shall interpret his meaning for you directly. The Heavenly Demon says, 'Today, this lowly Heavenly Demon has committed the great sin of daring to defy the great Ximen Qing.'"

Qing clenched her fist once more.

-AARGH! AAARGH! AAAARGH! Ugh, ugh!

Adjusting the strength with her grip, she managed to create a somewhat rhythmic beat.

It seemed the Heavenly Demon had some musical talent as well.

"'So you all should not defy Ximen Qing and serve her well on your own. This is what the Heavenly Demon implores you.'"

Then Qing clenched her fist again, and with an AAAGH!! the Heavenly Demon Spirit shattered into pieces.

"The end. So, did you hear? That's how it is. Of course, I don't have the talent to understand screams, so I just roughly called out what I thought he might have said. What do you think? Was I right?"

It was the wailing of a soul being torn out raw.

Paralyzed by that horrific sound, no cult member dared to step forward.

"We can just call him and ask. Yap, Heavenly Demon Summon!"

A triangular pyramid rose up on Qing's palm again.

"Aah..."

Zhi Shengzu lamented.

It was a scene of the Heavenly Demon Spirit, the soul of their great leader, being completely subdued and toyed with.

"Stop, please stop!"

"Alright."

Qing crushed the Heavenly Demon Spirit in her fist in one go.

With a short scream, the Heavenly Demon Spirit vanished.

She knew how to take it out, but didn't know how to put it back in.

But since it was only the Heavenly Demon that was hurting, why should she care?

"Doesn't the Demonic Cult believe in the law of the strong? From what I saw in the Bliss Palace, it seemed natural to eat your superiors and take their positions. So am I the Heavenly Demon now?"

Qing was just trying to provoke them further.

However, far from having hope drained from his eyes, Zhi Shengzu's eyes suddenly flashed with a strange light.

"Are you saying you have inherited everything from him?"

"You mean, like this?"

Qing roused the Heaven-Shattering Demonic Qi.

To be precise, it was the dregs of the Heaven-Shattering Demonic Qi.

Almost all of the Heaven-Shattering Demonic Qi had been compressed tightly with the Heavenly Demon and tucked away in a corner of her dantian, and only an extremely small portion had defected and newly joined Qing's True Qi Alliance.

Qing's hands were dyed with pitch-black Demonic Qi.

Originally, when manifesting Qi, there should have been a faint glow with the insides clearly visible.

But the Heaven-Shattering Demonic Qi not only didn't shine on its own, but rather ate light, painting a lusterless pitch-black void color.

And that wasn't all.

Countless eyes sprouted from Qing's black hands.

Qing looked at the most destructive Qi under heaven lingering on her hands and thought.

\textit{What the hell is this? It's disgusting and hideous.}

Qing withdrew her True Qi.

The Heaven-Shattering Demonic Qi, which had tried to impress its new owner only to be called ugly, dejectedly returned to her dantian.

"Heaven-Shattering Demonic Qi! Truly, you have...!"

"Wait a minute. What the… Hasn't the way you addressed me suddenly improved a lot?"

When someone says "you" (dangshin), it is considered speech used to speak to equals.

But when they say "you" (dangshin-kkeseo), it is several levels higher, becoming the highest form of honorific speech among honorifics.

The cult members murmured at this implication.

Qing frowned sharply.

"I have absolutely no intention of becoming the Demonic Cult's boss. Well, no. It might depend on the conditions."

"What do you mean?"

"Can't we at least live like decent human beings?"

Qing recalled her life in the Demonic Cult.

A city of hungry ghosts just devouring each other.

Because everyone except oneself was an enemy, they couldn't relax or trust for even a moment, so even when talking with smiling faces, in reality, they were just pretending to have relationships.

No person could become a source of good in such an environment.

Kindness comes from the granary.

When people are just red-eyed with vigilance trying to protect their own storehouse...

Who in the world could show compassion in such a situation?

"The law of the strong is over. Even without that, people naturally listen to the strong anyway. Stop slandering Zhongyuan now. Let's try living together. Send out letters to everyone and say let's reconcile. Say that we'll live like proper humans now, so don't start sword fights just because you see each other."

Qing thought of Jian Buxi, no, Ximen Xi, that lacking and not-so-kind Senior Sister Wannabe, now a Sister Wannabe.

How many Ximen Xis had existed in the Demonic Cult, how many had perished, and how many more would come to exist if things continued like this?

That was why a breeding ground for evil people shouldn't exist in the world.

It was too troublesome to kill them all off, and there might be idiots who became evil just because of their environment.

She said all this, but ultimately, difficult tasks should be passed on to others.

Fortunately, there was someone who seemed rather smart, yeah?

"That cannot be done! It would shake the very foundations of the Divine C-"

"Do you even have a future anyway? If I kill all of you here and go back to Zhongyuan, wouldn't the Demonic Cult be finished anyway?"

At those words, the tomb chamber fell silent once again.

Since the Heavenly Demon Supreme's realm was estimated to be the Life and Death Realm, to absorb that power, one would need to be at least in the Demonic Descent Realm.

Even if Demonic Descent and Unrestrained Realm were in the same league, Demonic Descent was actually considered about 50\% higher in strength.

In modern terms, it would be a 0.5 tier difference.

It wasn't a question of whether to accept the new Heavenly Demon or not.

It was a question of life or death.

In reality, it was all just bluster, though.

Qing was bluffing without actually having the ability.

\textit{This is how I'll get to go back alive.}

\textit{Might as well say what I want to say while I'm at it.}

Thanks to the Heavenly Demon parasite, her body had been reassembled into a top-notch latest model, but even so, her Enlightenment was still only at the Late Stage Peak Realm.

\textit{For heaven's sake! Oh heavens!!}

\textit{Why!}

\textit{Am I!!}

\textit{Still!!!}

\textit{Not at the Transcendent Realm!!!!!}

It was a cry that would make the heavens roll their eyes if they heard it.

'What the hell have you even done?' They would say.

Out of the forty-seven Heavenly Demon Divine Arts, all except three were locked, just taking up space in the Martial Arts Window.

Heavenly Demon Cultivation Art, Heavenly Demon's Reigning Step, and Heavenly Demon Finger.

These were the techniques the Heavenly Demon had used with Qing's body.

If she had known this would happen, she would have tried to induce him to use more techniques.

But well, they weren't gone, just locked.

When her realm rises, who knows what might happen.

She got three Purple techniques for free, so it would honestly be unconscionable to complain.

Moreover, by nature, she wasn't the type to regret losses particularly.

Even before her journey into Wulin, she was the type who would just think 'Oh well, can't be helped' when she lost something and then worry about what to eat for dinner.

Or perhaps it was a form of resignation trained by being born poor.

"Why don't you try establishing a country or something through this opportunity? Or maybe a Religious Sect Alliance? If you have power, you won't get beaten up when you go outside, right?"

"That is not something that can be spoken of so easily..."

"Well, that's for smart people to figure out."

Zhi Shengzu closed his mouth at those words.

\textit{You should know you're lucky.}

\textit{You're being spared because you're a smart kid and weak.}

\textit{Come to think of it, I guess all you did was talk back a lot. You didn't really cause any harm.}

However, there was someone who couldn't be spared.

Qing looked down at the former Alleged Natural Realm, who was now just a natural person.

The wreck who had suffered a double hit of mental shock and complete loss of Inner Qi was sprawled out with a dumb look in his eyes.

Just as Qing's gaze turned fierce.

"Wait! Please stop!"

"What? Why? I was just about to have some overdue fun."

"He is still the one who inherited the direct lineage of the First Heavenly Demon. As you said, he is an essential religious focal point for reorganizing the Divine Cult, so please show mercy."

"Tsk."

Qing clicked her tongue.

\textit{It would be a bit much to interfere after passing on all the work, yeah?}

Qing asked hopefully, just in case.

"Then, can I at least make him impotent?"

"Only his bloodline is important. Please cut off an arm or leg instead."

"That's the best thing you've said so far."

Qing smirked and squatted down in front of the Supreme.

Her white, slender palm gently caressed the Supreme's cheek.

Just as the Supreme's focus was slowly returning-

Qing's thumb dug into the Supreme's eye socket.

"ARGH!"

Of course, one couldn't help but scream if their eye was gouged out while they were alive.

But that wasn't all; Qing firmly held the eye socket with her thumb and palm.

With his head fixed without moving, only his body flailed wildly in pain.

The hands of an ordinary person without Inner Qi thrashed, hitting and scratching at Qing, but with her abilities boosted by Overhaul Rebirth, they couldn't even leave a scratch and were nothing more than meaningless struggles.

Qing finally smiled with satisfaction.

The sensation of piercing through the soft yet firm eyeball, the mixture of thick and thin substances inside wrapping around her thumb - it had been a while since she felt this tingling heat.

"Have you come to your senses? Should I pierce your other eye socket too?"

"I-It hurts, it hurts so much. Mommy, it hurts..."

"Tsk. You should use honorifics. From now on, you'll use honorifics with everyone in the world. You've been ill-mannered all your life, so you need to balance it out from now on."

Qing said with a bright smile.

The Supreme looked up at Qing's face, trembling in pain. His one remaining eye perfectly reflected Qing's beautiful smile.

"I-I underst... I understand."

"Good boy. That's right. Who's a good boy?"

Qing's thumb popped out of the Supreme's eyelid.

The unknown contents of the eyeball dripped down.

"Urgh, kkeup..."

The Supreme gritted his teeth and endured the pain.

Qing tilted her head and thought.

\textit{What's this? He's holding back his screams? Does it not hurt enough?}

\textit{Should I have just pulled out the whole eyeball?}

But the Supreme's appearance was already in a pathetic state.

Remembering the scene she saw in the Formation, her excitement completely faded.

Also, now he's just a commoner who doesn't know martial arts.

Qing wiped her sticky thumb on the Supreme's head.

She wiped off the sticky foreign substance by rubbing it front, back, side, and front again.

While cleaning her hand like that, she spoke.

"Consider this forgiveness for trying to burst my eye after punching me in the stomach. From now on, just keep being a good little boy. Then, even if we meet again, we can look at each other with nice smiles. You understand what I mean, right?"

'If you're not a good boy, I'll look at you with a… bad smile.'

That was essentially the message Qing was trying to convey.

And she delivered such a chilling warning in a gentle voice.

The Supreme nodded blankly.

With that, Qing completely let go of her hatred.

The kid's state has become completely derpy.

\textit{Are you kidding me? All I did was pierce one eye. Boring.}

At any rate, now that she had neatly finished her revenge, she had done everything she needed to do.

Qing headed towards the exit of the tomb chamber with clicking steps.

"Hoit. Alright then. Take care of the rest yourselves."

Qing waved her hand behind her back as she slipped into the stairway leading outside and disappeared.

It was the end of her insufferable kidnapped life.

