\chapter{Heavenly Demon Tomb (5)}

Zhi Shengzhu's eyes trembled slightly.

Though his expression didn't change, it was clear he wasn't as emotionless as he usually was.

"What do you mean 'why'? If it is because you are fond of the Formation's illusions, I shall tell you that in the end, it is all fake. You shall starve and wither away. Are you saying you do not care if you die such a miserable death?"

"What are you talking about? When did I say I wanted to die?"

"Just now, you..."

"Aren't you going to dismantle the Formation? Why should I do it when there's an expert here? Imma let our little kiddo do all the annoying and difficult work. Go ahead and do everything you want."

Zhi Shengzhu's mouth just opened and closed.

\textit{What shameless words!}

"There is a limit to how thick-skinned one can be. Are you seriously saying you will not help but still wish to reap the benefits?"

"Yeah. It's not like I'm the one in a hurry, right?"

"That, that's..."

"Besides, even if I wanted to help you, kiddo, there's a reason I can't. I really have no choice."

"What could that reason possibly be?"

"I don't take orders from those weaker than me."

Zhi Shengzhu's expression soured.

"Damn it. Bullshit. What kind of bitch is this!"

"Hello? I'm right here. Since you said that, now I'm thinking maybe I'll just stay here. Though the floor might be a bit cold to lie down on."

Qing giggled as she taunted him.

Zhi Shengzhu's face turned bright red.

Then Qing suddenly turned serious.

"Hey. I might be ignorant, but I know how things work, you know? What can you even do with an idiot who knows jack shit about Formations?"

"That's..."

"You'd have me lend my strength, right? But isn't that all? If we move separately, it'd be better not to touch anything at all. If we move together, it's not much different from you doing it alone, is it?"

Zhi Shengzhu tightly shut his mouth.

It was always the ones with nothing to say who just closed their mouths.

Qing had her own experience in production work.

This meant she had experienced saying her goodbyes to countless newbies passing through.

A newbie who knew nothing wasn't really much help even if you take them around.

But if you leave them far away and have them work separately?

That day would be the day the production yield gets properly fucked in the ass.

Similarly, with Qing herself being a newbie who knows nothing about Formations, what was the point of dragging her along?

All it looked like was a ploy to keep her close and monitor her, afraid she might crack some Demonic Cult heads when he wasn't able to see.

Qing was merely ignorant, not stupid.

From the start, she was a cunning bitch who clearly distinguished between those she could mess with and those she couldn't, thus changing her mask accordingly.

It was not that she particularly tried to act smart.

It was just that acting on her whims often resulted in stupid actions.

Nevertheless, she was a proud female swordsman of Wulin who had somehow survived all this time with such a conduct!

Her indifference to learning anything unless absolutely necessary, despite her ignorance, could certainly be considered fucked up as a member of the human species, though...

"Won't you go and dismantle the Formation for me? I'll just rest here for a bit. Oh my, my legs feel a bit numb too,"

Qing said with a vile smile.

Zhi Shengzhu breathed heavily, then finally let out a deep sigh.

"...Fine. In return, please do not lay a hand on the Divine Cult members."

"Well. I wonder. What to do?"

"There is no need for you to build unnecessary resentment, is there not? That is, if you wish to walk out of here in one piece when this is over."

\textit{Then can't I just kill them all before that?}

Qing was thinking this when...

"The depth of the Formation varies depending on the person. If you clumsily disturb it and they wake from their illusions, there are several individuals that a mere Transcendent Realm martial artist could not possibly handle."

"Shit. That makes sense."

\textit{I mean, just look at this kiddo walking around with his shit together.}

\textit{There's no guarantee the other Demonic Adepts aren't like this too, right?}

Moreover, if she decided to split a Demonic Human's head, she'd have to completely shatter it to literally remove the root of the 'problem'. And if she failed, it could cause big trouble.

If she didn't split them, at least she could return even if she lost the Heavenly Demon Spirit.

In that case, there was no reason to choose the former.

Qing scratched her head vigorously.

Then, out of habit, she untied her messy hair and tied it up again as she frankly admitted.

"Alright. I'll just quietly look around then. So, how long will it take? Shouldn't an expert like you have a rough idea?"

"Well. With good luck, it might be possible within one dagyung, and with bad luck, we might all starve to death here."

"If you don't want to tell me, just say so. Seriously, the way you brainy types talk..."

Qing grumbled as she turned around.

"Where are you going?"

"To look around. What about it. Why do you care."

Actually, she was going to search for the Heavenly Demon Spirit.

It didn't seem like this would be a quick job, after all.

"It could be dangerous if you get caught up in the Formation."

"What? Are you worried about me or something?"

"As if. I have given you a clear warning, so handle yourself accordingly."

With those words, Zhi Shengzhu turned and left first.

\textit{He's pissed off. Pouting, maybe?}

Qing shook her head and looked around the great hall.

Besides the door she came in through and the one the kiddo left through, there were seven more doors.

\textit{Should I use the left-hand rule?}

It was a simple logical inference that any maze could be solved by keeping your left hand on the wall and following straight.

As such, Qing headed towards the leftmost door.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It felt like half a day had passed.

But all Qing had learned was a tiny bit of knowledge about other people's illusions.

The illusions ultimately fell into two categories.

Those with great desires seemed to enjoy seeing themselves achieving success in a future that hadn't yet come.

And then there were people who lingered, searching for what they had lost from the past.

Even if it was just food, didn't Qing herself belong to the latter category?

In that sense, peeking into other people's illusions wasn't particularly fun.

Expressing it as seeing hopes for the future might sound cool, but in the end, it was just childish delusions hidden deep inside.

As for people seeing the past, well…

Qing had no interest in the stories of people she didn't even know.

Moreover, the search had been fruitless.

In fact, how could there be results when she was looking for an object she didn't even know the appearance of?

Bluntly speaking, if it looked like some random stone, Qing might not be able to find it even if she spent decades searching diligently.

\textit{Shit. Nothing's going right.}

Qing grumbled as she crossed a vast prairie where waterfalls flowed and herds of horses grazed.

Then suddenly, as the deafening sound of rain roared loudly, she came to her senses and found herself standing in the middle of a dark downpour.

For Qing, who had already broken through the illusion, it was just a phantom she could pass through. However, just hearing and seeing the rough rainstorm was overwhelming enough.

And in the middle of it all, someone was sitting.

Holding someone in their arms.

As Qing approached, she saw a familiar face.

Cui Liweng was holding his daughter's corpse in his arms, endlessly staring at her face.

All while his body continued to be beaten by the pouring rain.

Qing watched this scene for a while.

It was like looking at a completely frozen photograph, except for the streaks of rain.

Only the occasionally blinking eyelids, covering the old man's regret-filled gaze, moved.

The time Qing spent coming in, eating, and fully enjoying the sweets was not short at all, and she felt like she had wandered around for half a day after that.

But even so, Qing could easily tell that Cui Liweng had been holding onto his daughter's cold body like this for that long of a time.

Qing frowned.

\textit{If you're in an illusion, can't you see a more hopeful scene and heal your body and mind?}

\textit{Agh shit, old man, stop being so mopey.}

"Hey, look here, Gramps."

Then Cui Liweng looked up at Qing blankly.

"Why don't you look at a brighter, more joyful, and happier scene? If you're going to see your daughter's face, at least recall some good memories."

Then the scenery changed.

In a magnificent flower garden, a young child chased butterflies, letting out clear, childlike laughter.

All the while, she kept glancing this way, clearly checking to make sure her daddy hadn't gone anywhere.

"Yeah. That's much better to look at. You don't have many days left to live, so choose good things to see and have a peaceful death. Don't be all pitiful and miserable."

Cui Liweng stared at the scene as if entranced.

Then suddenly, he blurted out.

"No. I cannot."

And it returned to that scene.

The rain was falling, the old man was getting beaten, and the daughter was dead.

Qing got irritated.

"What's the problem? What's wrong with you?"

"The child took her own life."

"I know that. I heard it last time too."

"Isn't one's own life the most precious thing to anyone? Even if life is hard and difficult, that should still be true. But for her to throw away her own life, she must have found even the act of breathing painful."

"So, you want to be in pain together?"

Cui Liweng burst into bitter laughter.

"The child's wish was to go to Zhongyuan. I do not know who put such ideas in her head, but she believed her happiness was there."

"And?"

"At that time, this old man was the Great Guardian of the Divine Cult. Would a Great Guardian have any reason to leave the Demonic Cult? As far as this old man knew, Zhongyuan was a hell where parents exchanged and ate each other's children."

What father in the world wouldn't stop his daughter from going to such a living hell?

Moreover, Cui Fangcai was the daughter of the Great Guardian, a leader among the Divine Cult that was hated by all of Zhongyuan.

"She was a good child. She could not say a harsh word to others, always losing out herself instead."

The child changed day by day.

Qing watched that growth through this ever changing world.

The daughter who used to tear up at the sight of someone getting hurt, empathizing with their pain, now just spewed harsh words at everyone with eyes full of venom.

But her true nature hadn't gone anywhere.

Because all that viciousness was just scratching at her own heart.

And so, Cui Fangcai eventually took her own life.

"Only after my daughter died did I step down from my position and volunteer for Outer Hall duties. I wanted to see with my own eyes what Zhongyuan, which that stupid brat had longed for, was really like. To mock her, saying she did not know how fortunate she was, how happy her circumstances were because of whose daughter she was born as."

It was only after going to Zhongyuan that he realized.

The child had been right.

He should have let her go.

At the very least, this jar of Gu where everyone devoured each other to only grow their own poison - this Divine City - was not a place suited for the child.

She might have been happy anywhere but the Divine City.

Cui Liweng looked at his dead daughter's face again.

Qing finally understood this scene.

Cui Liweng was already an old man who had died a long time ago.

The reason he was still breathing was just to suffer.

It was a punishment a father who believed he had killed his daughter was inflicting on himself.

That was why his desired wish looked like this.

His wish must be to lock himself in the most painful and agonizing time of his life.

Just begging his heart to be torn apart endlessly.

Can such a life even be called living?

Qing messed up her hair vigorously.

Immediately tying it back up again had no meaning, as it was actually an action she had taken because she felt uncomfortable.

"I seriously hate melodrama."

\textit{But is this really the old man's fault?}

\textit{Is it really such a big mistake that he deserves to suffer like this for his entire life?}

\textit{While I can understand his feelings...}

Qing looked at the Purple Lightning Demonic Warlord's Evil Karma.

And she saw that gaze fixed on his daughter.

\textit{Whether it turns out well or not, I guess it's the old man's fate. His karma.}

\textit{But that doesn't mean I want to leave this unsightly scene as it is.}

\textit{My education is too short to provide psychological counseling.}

\textit{But physical therapy is my specialty, ain't it?}

Qing raised her hand, which held Fushen-di, high.
