\chapter{Heavenly Demon Tomb (3)}

It was the night before Pingshan Lake.

\textit{It's not just kimchi stew that I want… I want to drink cola too.}

\textit{Even if it's not cola, that's fine.}

\textit{I just want to drink an ice-cold carbonated drink.}

\textit{I wish I could chug it until my throat bursts.}

\textit{But carbonation would be impossible no matter what…}

Qing's longing grew even stronger.

And how could her condition possibly improve when she was yearning for something that didn't exist in this world?

As she was staring blankly at the bonfire, lost in thought…

"The Supreme wishes to see you tonight."

The kiddo she hadn't seen in a while was still as small as he had always been.

Qing shook her head halfheartedly.

"I don't really wanna…"

"The Supreme did not ask for your opinion. It would be better if you quietly foll-"

"This girl has said she does not want to."

Cui Liweng cut off Zhi Shengzhu's words.

"Purple Lightning Demonic Warlord. The Supreme-"

"Isn't it about time we stop coddling that grown brat? We've come this far, so what else can he do? We've already indulged him in the Divine Cult because he throws all sorts of tantrums if we don't listen to him."

Zhi Shengzhu sighed deeply.

"Damn it. Such bullshit. Please cut me some slack. I've been stuck next to that bastard for five years. Can't you go with her and sass him yourself, Purple Lightning Demonic Warlord?"

It was a surprisingly disrespectful remark.

Cui Liweng flinched at this.

In fact, the current reality was that all the high-ranking members of the Divine Cult were grateful to Zhi Shengzhu.

The Supreme was the very embodiment of the two words; "arrogant" and "rude". So much so that he had no one besides him.

And Zhi Shengzhu was the very boy who had somehow managed to prevent the worst of his atrocities by gently coaxing him. So, they could not help but appreciate him.

"It's not that I do not understand the difficulties of the Demonic Brain, but just look at this state. The child is sprawled out like a three-day-old rotting goat carcass, having fallen to her Inner Demons."

At those words, Zhi Shengzhu's eyes widened in surprise.

To Zhi Shengzhu, Qing had been an unparalleled madwoman who grinned while cracking the skulls of the Covert Operations Division's assassins.

"That state was because of Inner Demons?"

"Can you not see this condition?"

"I thought it was a ploy to induce carelessness. Didn't you clearly see the bloody murders during the previous transport, Purple Lightning Demonic Warlord? However, this will be a good excuse to give to the Supreme, at least."

Zhi Shengzhu sighed deeply and turned around.

He headed straight for the luxurious tent, where the Supreme could be seen lying on his exclusive silk bed.

The Supreme, who had just finished a big yawn, asked.

"You came alone?"

"I apologize for reporting this, but Ximen Qing is said to be in a state of Inner Demons, so I confirmed such a fact and returned."

"That bitch?"

The Supreme smirked.

"Have you seen that bitch's eyes before? Do you know what I saw in them?"

"I would like to hear your esteemed opinion."

"Even the great Secret Pavilion Leader does not know how to read people, probably because your realm is so low. Let this elder properly guide you. I have never seen such intense hatred in my life, you see."

Zhi Shengzhu recalled the image of Qing lying sprawled out on blood and brain matter.

Even now, thinking about it sent chills down his spine.

The Supreme giggled at that expression.

"She is not someone who will ever break. And that is precisely why it is fun to break her. I guarantee you, it is all an act."

"If that is the case, should I call her back?"

"Well. It's fine. Since she's throwing a tantrum, I can overlook it this once. Along with the Secret Pavilion Leader's failure."

Zhi Shengzhu thought to himself.

\textit{There probably won't be a second chance.}

But he hid those inner thoughts and bent his waist in the shape of a sickle.

"Thank you for your great mercy. O' Supreme."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When looking down from the highlands, the view of Pingshan Lake Grand Canyon was simply breathtaking, and it didn't actually look that complicated.

But once you set foot in the winding crevices of the canyon, anyone would be taken aback.

In essence, people couldn't get their bearings on the gloomy ground where sunlight barely reached.

With no straight paths and visibility limited to just a few zhang ahead due to the winding cliffs, it didn't take long before one got lost and started wandering.

Of course, for Masters, it was not such a dangerous terrain.

Such superhumans, able to easily climb cliffs tens of zhang high, could simply climb up the walls and look at the sky to find their way home if they really got lost.

That was why the entrance to the Heavenly Demon Tomb was hidden in the shadows under an outward-leaning cliff, where sunlight never reached year-round.

Being in the middle of the Grand Canyon, even if someone wandering stumbled upon it, they couldn't return to report it, and Masters would climb up the cliffs to escape, so they had no reason to venture deep into the canyon floor.

As such, the Demonic Cult was only able to find it because they knew the Heavenly Demon Tomb was in Pingshan Lake, thanks to the Celestial Martial Emperor's record.

Otherwise, it was a place they couldn't have found even if they searched for a thousand years.

Qing, cradled in Cui Liweng's arms, looked at the entrance of the Heavenly Demon Tomb and thought.

\textit{It's kind of... underwhelming.}

\textit{Something… More grand than... Ah, whatever. Who cares.}

A small stone door, barely big enough for two grown men to enter side by side with their shoulders touching, was leaning against the cliff, almost lying down.

It wasn't hard to guess that there would probably be stairs leading underground behind it.

Realistically speaking, who would put a huge, dazzling golden door on a treasure vault?

That was a scene you'd only see in adventure movies back in Qing's homeland. If one was actually worried about thieves, it was only natural to hide it thoroughly.

It was the same reason why the Heavenly Queen's tomb was sealed in a stone chamber under a wild hill without even a tombstone.

Qing put the Fushen-di to her lips.

Though there was an upbeat arrangement she had worked hard on, because Qing wasn't very cheerful at the moment, it was just the original Heavenly Heart Harmony played sorrowfully.

As the Imagery of the song matched Qing's longing heart, even the extremely evil Demonic Adepts couldn't avoid being moved by the waves of emotion, accompanied with the world's most beautiful sounding instrument.

As some even had tears welling up in their eyes, the unusually mournful flute sound quietly came to an end.

And then, thunk. Thunk thunk thunk...

A dull sound of something falling from the stone door reverberated, growing increasingly distant.

The Demonic Cult's mechanism expert carefully stuck to the stone door, tapping, probing, and listening, as if investigating. Soon after, he looked back and spoke.

"It seems the locking mechanism has been released."

Qing, already deflated, deflated even further.

With this atmosphere, she thought the door would automatically open with a dramatic Dududududu after playing the flute.

But all that happened was a mere lock falling off. Moreover, even that just rolled away far inside, unable to be probably seen.

If the mechanism expert had known her thoughts, he would have jumped in shock.

A door that unlocks with a specific sound - it was truly a peerless artifact that only Banchi could have made.

Moreover, who knows what mechanisms might activate if forcibly opened? The fact that it unlocked so simply was actually a sign of much more sophisticated craftsmanship.

The expert pulled on the stone door's handle, and it opened with a creaking effort.

A pitch-black hole gaped open.

When they threw in a spark, it revealed, as expected, rough stairs leading downward.

And then the advance team, consisting of mechanism experts and tomb raiding specialists, packed up their gear and headed inside first.

Qing was a bit taken aback.

\textit{Uh. Wait.}

\textit{If it's like this… If they find the Heavenly Demon Spirit first and bring it out, won't I be left high and dry?}

In Qing's mind, she thought everyone would enter together, deal with all sorts of intricate traps and unknown monsters, and go through hardships.

And at the end, when they opened a brilliant golden door, they would face a glowing treasure bathed in a beam of light amidst mysterious smoke of unknown origin.

Then, only then, would the miracle of the cripple suddenly standing up occur, followed by her grabbing the Heavenly Demon Spirit, staging a hostage situation to escape, and then spectacularly destroying it.

This was Qing's plan.

But realistically speaking, would the cult's core members really just barge in, knowing what's inside?

This was exactly why video games were so harmful.

What could be more absurd than video games, after all? You know, those games where you enter someone else's house, open chests, boldly take things right in front of the owner's face, and even strike up a conversation all while doing so? How fucking ridiculous.

And this very result was what happened when you try to understand the world through video games.

If Xue Ganom had known Qing's plan earlier, he would have been unable to hide his gaze, telling her to live in reality and stop listening to the tales of scam artists. He would have found her utterly pathetic.

"Haa. Gramps, can you put me down for a moment?"

"Careful now, watch your step."

Cui Liweng carefully set Qing down.

He was truly a devoted old man.

Qing stood with her feet on the ground.

\textit{Yeah, I still have no motivation whatsoever.}

\textit{But I have to do this, don't I?}

\textit{Is this... really something I have to do?}

\textit{Why me?}

Someone deep inside Qing protested.

\textit{Why do I have to do it?}

\textit{Well, if I don't stop the Demonic Cult bastards, the Divine Maiden Sect and incidentally the innocent people of Zhongyuan will suffer-}

\textit{Why do I have to stop them?}

\textit{Because I opened it with the Fushen-di-}

\textit{Wouldn't it have opened anyway, even without you?}

\textit{If you hadn't stolen the Fushen-di?}

\textit{The Demonic Cult bastards would have opened it anyway.}

\textit{If anything, I've killed a bunch of Demonic Adepts, so shouldn't I be praised a hundred times over just for what I've done so far?}

\textit{Huh?}

\textit{That's right...}

\textit{I'm just... even breathing is a struggle for me in this disgusting neighborhood… This neighborhood I know nothing about...}

Qing's shoulders slumped.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The original name of the Heavenly Demon Tomb was said to be Simunai\footnote{Nai's resting tomb}.

It was a mausoleum Banchi built longing for his deceased wife, and at the same time, his own tomb.

Banchi had taken his own life by poison after finishing the installation of the mechanism formations inside.

The important thing was that Simunai was built after the Heavenly Queen's death.

What if the door to Simunai opens?

It meant the door was opened by playing the Fushen-di.

And playing the Fushen-di meant that his beloved wife's tomb was desecrated.

He was a man who took his own life out of longing for his wife.

There was no way he could forgive such a brazen person who desecrated his wife's tomb.

Of course, he couldn't have predicted that later, a madman called the Celestial Martial Emperor would ignore the perfectly good entrance, split the earth, break through the ceiling to enter, and gently place one precious looted item inside.

Someone of the Celestial Martial Emperor's caliber could use his Qi Sense to find the mausoleum and then create a shortcut without even touching the complicated mechanism formations.

At any rate, Banchi's wrath began with the opening of Simunai.

He had planted a large iron ball in the locking mechanism designed to unlock with vibrations of a specific pitch.

And now.

The lock has been released.

The iron ball fell, tumbling down the stairs with a series of thuds, and burrowed into a deeply carved groove.

The ball rolled along the slanted groove.

As the rolling ball struck other iron balls, it set them off in different directions along other carved grooves.

The number of rolling balls increased.

As the balls struck other balls, they flowed down dozens, hundreds of branching grooves.

Some balls pulled strings, while others pushed and pressed rods, completing the final operation of the mechanism, Banchi's final formation.

Banchi's posthumous work.

It was the activation of the Phantasmal Maze of No Return Formation.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Sniff sniff.

Qing suddenly flared her nostrils.

"Child?"

"Gramps. Don't you smell something?"

"Smell? What is with this sudden talk of smells?"

Qing was serious, however.

This familiar scent tickling her nose, so familiar it felt like tears might burst forth at any moment… That scent that would hit her when she opened the front door of her home in Seoul, her mother's...

"Kimchi stew!"

Qing shouted and dashed off.

And then she slipped right into the entrance.

"Huh?" "Huuh?" "Huuuh?"

Everyone was dumbfounded by this miraculous sight.

Qing was already the ideal type, as well as the visual oasis, for the Demonic Cult Masters.

Following her amazing flute performance, where everyone's attention focused on her, they then witnessed the sight of a cripple (well, not exactly, but rather more like partially lame) dashing off with a Qinggong Technique.

So they could only blink their eyes, rub them, and gape stupidly, wondering if this was a dream or reality, and what on earth kimchi stew was and why she ran off shouting for it so desperately.

What snapped everyone out of their daze was the old man's scream of shock.

"Heavenly Demon Spirit! No! Fangcai! Cui Fangcai! Come back!"

Cui Liweng screamed as if his intestines had been cut and chased after her.

"Keuhaha! Yes! I told you! I knew this would happen! As expected! If she is to be my woman, she should have this kind of side to her!"

The Supreme laughed maniacally as he ran off.

"What are you doing! Hurry up and chase after them!"

Zhi Shengzhu shouted angrily.

At that, the Demonic Cult Masters increased their speed and poured into the Heavenly Demon Tomb.