\chapter{Heavenly Demon Tomb (9)}

"O' Great Heavenly Demon Supreme, here is your true Divine Blood."

"I have already achieved my Second Coming. Moreover, why should I take an inferior tool when I have a better one, even if it carries Divine Blood?"

"However, this is what I prepared for y-"

"Enough. Could it be that this child is precious to you?"

"She is... my inadequate daughter."

But the Heavenly Demon shook her head.

"That cannot be. The acupoints are no longer those of a living body; it is nothing but a demonic entity with dead blood flowing through it. How can you call it a human's daughter? It is merely a corpse with its soul having already departed."

According to the Book of Rites, one of the Five Classics, humans were composed of Hun and Po.

Hun was the spirit and soul, thus called the mind.

Po was the flesh and matter, thus called the body.

So when a person dies, the Hun ascends to heaven, passes through the underworld, and enters reincarnation, while the Po becomes a corpse that falls to the ground, decays, and merges with the world.

When the body dies, the soul naturally departs.

But very rarely, the opposite happens: the soul dies and only the body remains, with the heart still beating and breath still flowing.

But how long could a body even last without a soul?

Even if one breathes life into it with utmost care and forcefully mashes food down its throat, it cannot survive past the forty-nine days it takes for the Hun to enter reincarnation and disappear.

However, there was a joke among Jiangshi Sorcerers.

If you keep a soulless body alive until the exact moment it takes its last breath on the forty-ninth day, couldn't another soul enter due to a mistake in the netherworld, and the dead person be reborn as a living one?

It would be a living corpse with dead blood flowing through it.

Since all toxins act on the blood, what more harm could be done to blood that was already dead?

Originally, the most difficult part of creating a Jiangshi was the damage caused by the toxicity of the drugs.

But what if it didn't deteriorate from the toxicity even when doused with the world's most potent drugs?

It was a joke that contained the wishes of Jiangshi Sorcerers.

The Heavenly Demon didn't know such details, of course. Nevertheless, she could still tell that the spirituality of the blood had already died just by observing the body.

However, it wasn't like Cui Liweng's current state was normal either.

"That is right! My child had already died but returned like this! Please take pity on a father who has already lost his child once..."

The Heavenly Demon sighed deeply.

"I have existed in this world for my entire life, rejecting even death, all for the sake of the cult's long-cherished wish. It is to completely slaughter those detestable oppressors of Zhongyuan and achieve true liberation."

"But..."

"Now that I have such a body, there is nothing to fear in the world, and the time has come to fulfill our wish. Are you saying I should give up on our great cause for your personal feelings at such a time?"

"The body I prepared for you is surely enough to..."

"Do you truly think so?"

"Please, I beg for your mercy."

The Heavenly Demon glared at Cui Liweng with Qing's face.

Everything in the Heavenly Demon Divine Cult came from the Heavenly Demon. Even its cruelty. As such, her reaction was all too obvious.

"Is a mere connection in the human world so precious to you? Your heart has already left the Divine Cult. How dare you stand before the representative of the Heavenly God and Demon God with your head raised, having turned your back on the doctrines and commandments?"

The Heavenly Demon was called such because she was the incarnation of the Heavenly God Ahura Mazda and the Demon God Angra Mainyu.

She was also the incarnation of a god of destruction who abandoned the Heavenly God's creation of life and took the Demon God's power to crush the outdated oppressors of Zhongyuan.

And the anger of this very living god was directed at the old Great Demonic Adept.

Cui Liweng trembled.

But even in the midst of that, he cried out indignantly.

"A mere connection in the human world, you say! How can you say such a thing! You too are human! How dare you claim mere martial arts intertwined with Imagery as divine power!"

The day the Demon God had set to destroy the world was still billions of years away, at the end of eternity.

Any end that comes before that is not the will of God, and moreover, there is no reason for God to want to destroy the insignificant Zhongyuan.

As such, the Heavenly Demon was human.

Just a mere human clumped together with hatred for Zhongyuan.

Martial arts were human tools that recreated nature through Imagery, so wasn't it laughable to pretend to be a representative by imitating the Demon God?

That was essentially what Cui Liweng was saying.

"How dare you!"

The Heavenly Demon raised a finger and pointed at Cui Liweng.

She had surpassed the Transcendent Realm and achieved Overhaul Rebirth, but as the body was still young, she hadn't undergone Body Reconstruction yet. As such, it was unknown how far the Heavenly Demon's martial prowess had risen.

However, the pitch-black Force gathering at her fingertip already contained an absolute destruction that could not be blocked by the martial prowess of a ‘mere' Unrestrained Realm Master.

The Heavenly Demon Finger. It was the infamous Force Arts of the Heavenly Demon Divine Art.

Black death extended from her fingertip.

The straight line of Force that stretched out did not aim for Cui Liweng's head.

Suddenly, a Demonic Cult member who had been lying prostrate to the right of her outstretched finger exploded.

Human debris scattered in all directions.

Cui Liweng looked back and forth between the Heavenly Demon and the blood stain left behind in the shape of a sun during an eclipse.

"...?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing, holding the mouse, muttered in disbelief.

"What the hell? Suddenly shooting laser beams? Is this even allowed in wuxia?"

\textit{Of course, Wulin had a fuckload of outrageous things when I experienced it firsthand. But even so, isn't shooting lasers a bit much?}

\textit{Shouldn't it at least pretend to be some kind of martial art?}

\textit{Even Master always rode on a sword when flying around, to at least keep up a pretense. Then, she could at least insist it was something similar to swordsmanship.}

\textit{But if you stretch out your finger and a laser beam comes out, isn't that more of a robot rather than a human? Or maybe a lich or some other endgame monster that could be categorized as a Mage.}

For reference, this was actually the first time Qing had controlled this game with a keyboard and mouse.

She had been thrown into Wulin right after creating her character, so she hadn't actually enjoyed the main game for even a second.

It went without saying that she didn't know the control keys.

As such, she was in the middle of pressing various buttons. And when she saw that the old man was about to die, she frantically clicked all over.

Fortunately, even though it was a game made by uncivilized Chinese, it adhered to the fundamental control method of right-clicking to target enemies.

\textit{Even though they're fucking plagiators who don't even follow international law, should I at least praise them for matching international standards for the game interface?}

\textit{Or should I say it's typical of those uncivilized Chinese who consider plagiarism a virtue? Maybe they just copied and pasted a familiar UI?}

At any rate, Qing was a skilled gamer.

And following this logic, this also meant that being able to quickly adapt to basic controls without seeing instructions was very, very easy for her.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The black beam repeatedly sliced through the air.

Every time she pointed a finger, it hit with 100\% accuracy, causing Demonic Cult members to explode.

Even middle-aged managers who massacred countless belly buttons with their dad jokes couldn't physically make people explode, so this truly could be called a godly move befitting a superior.

The Heavenly Demon shouted angrily.

"W-What are you doing! Stop this immediately!"

But her body moved on its own; suddenly her legs stepped in a strange footwork pattern, her knees gave quick beats of momentum, her waist twisted, and her arms swung.

It was the dazzling dance of a K-pop boy group that shook a world different from Zhongyuan, boasting of their bulletproof  nature\footnote{BTS}.

Then suddenly the dance stopped, and she jumped back and forth, side to side, front to front, side side side, shaking her body in a dizzying manner, before spinning rapidly in place.

The Demonic Cult members pretended not to see the Heavenly Demon's crazy actions, gritting their teeth and maintaining solemn expressions.

"You wench, stop it, I said stop it! Behave yourse-!"

The Heavenly Demon suddenly recalled the True Qis stuck in the Upper Dantian.

They seemed to be tightly wrapping and protecting something.

It must be the original owner's soul hiding there.

The Heavenly Demon roused the Heaven-Shattering Demonic Qi.

Demonic Qi in the form of a hideous shape with eyes densely packed became a high tidal wave, devouring the meridians and boiling violently.

A powerful hostility, the realm of which was not in the least decipherable. This massive flow created through countless lives, charged forward with spearheads raised.

Compared to that, Qing's True Qi was merely a handful.

Qing's True Qi, regardless of Yin and Yang or Orthodox and Unorthodox, united as one in the face of crisis. They tightly embraced each other and built a wall in preparation for the impact.

And then, BANG!

Unfortunately, the difference in Enlightenment was also a difference in level.

As such, there was too great a gap between Qing and the Heavenly Demon's levels.

Qing's True Qis crumbled in one hit.

The Heaven-Shattering Demonic Qi wedged into that gap and burrowed in.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

BOOM!

Qing, who had been giggling while holding the mouse, was startled.

Anyone would be startled if they saw a strange person appear by breaking through an one-room apartment wall.

At the same time, a reflexive scream burst out.

"No! My deposit!"

The man who had broken through the wall scanned the surroundings.

He was wearing only a pair of shorts on his broad shoulders. His exposed upper body was so densely covered in scars that it was hard to find a spot without them.

Qing, a common citizen whose knees would go weak just at the sight of tattoos, was faced with something even worse: traces of surgical procedure tha resulted in full-body mutilation.

Qing tucked in her neck and spoke.

"Um, coming all the way here is, how should I put it... a bit unfair, isn't it? It's kinda cheating. Are you for real right now? Breaking through walls and coming for an IRL fight just because of a little prank is too much, don't you think?"

"You seem more cowardly than I thought. When I lost control of the body, I expected a more dignified soul to shine through."

"Hehe. Well, you know how it usually is... Everyone hiding behind a screen is a third-generation chaebol who graduated from Seoul National University, got their master's degree, claps pro gamers silly, and is a cute girl who's completed military service..."

"Ha. I do not understand what you are saying, but I can tell you are not even worth dealing with."

At that, Qing smiled awkwardly.

"Of course, of course. Don't mind me and just continue with what you were doing. I'll just stay here quie-"

Qing couldn't finish her sentence.

Because people who have their heads exploded can't continue speaking.

Qing's headless body fell from the chair and rolled on the floor with a splat.

Bright red blood spread across the yellow linoleum.

The Heavenly Demon stretched his mouth into a smile and closed his eyes.

And at the same time, the Heavenly Demon opened her eyes.

She slowly curled her fingers one by one, finally clenching her fist tightly and turning her head.

Her wrathful gaze was directed at Cui Liweng.

"Your wench of a daughter was quite insolent."

"W-What..."

"If she hadn't acted up, she could have at least lived on in consciousness to witness our great cause. This must also be because the father failed to educate her properly."

As Cui Liweng's expression became wrought with despair, the Heavenly Demon again spread her fingers.

Pitch-black Force was released from her fingertips, forming a spherical Force Compression, and a destructive straight line extended out.

Cui Liweng simply closed his eyes calmly.

Then…

It missed!