\chapter{Heavenly Demon Tomb (1)}

"Senior Sister, how did it go?"

"Eung? How did what go?"

"I mean about Xue Ganom. The one with 'toilet' written on his forehead."

"Ah! That guest? He said he doesn't sleep with Bliss Palace disciples. 'No matter how desperate I am, I do not want to be under a temptress. Ah. Sorry if that offended you. It's just that my life is precious to me.' Was what he said and stuff."

Qing was startled.

Jian Buxi had almost perfectly imitated Xue Ganom's voice.

The realism of the imitation was so good that even Qing might have been fooled for a moment if she hadn't seen her face.

\textit{What the heck?}

\textit{This Crutch is this talented when it comes to voice mimicry?}

\textit{Also, it was possible for someone to have a talent that's so utterly useless even if they have it?}

Qing marveled at this worthlessness anew and asked.

"Not that. Are you going to Zhongyuan?"

"Huh? I told you last time, didn't I? I said I'm going."

Her tone suggested it was obvious and questioned why Qing was even asking.

Qing clutched her chest in frustration.

"No, what? What about Xue Ganom do you trust so much? Aren't you suspicious at all? You're just going to follow a stranger like that?"

"Huh? Isn't he your friend? Is there another Xue Ganom with 'toilet' written on his forehead?"

"Well, that's true, but..."

Xue Ganom said he would move to the Yunnan region.

Yunnan is geographically close to Zhongyuan, attached below Sichuan on the map.

However, there was a difference that couldn't be seen on maps - its altitude.

It was a land belonging to some of the highest mountain ranges in the world.

Moreover, it was a land difficult for people to live in due to its knife-like mountain terrain.

It was so extreme that there was even a joke about seasons changing with every step one made.

And it was actually true. After all, taking one step off a vertical cliff could change winter to spring, and another step on a protruding part could reach the summer that was far below.

"Ah! He asked me to tell you this. 'Though our acquaintance was brief, I can say it was quite an enjoyable time. If fate brings us together again someday, let's have a drink.'"

"Well. Can you tell him I'm grateful too?"

"Okay!"

Xue Ganom, dreaming of escaping the Demonic Cult, couldn't directly meet with Qing, who was essentially a VIP guest.

But that's life, isn't it?

\textit{Farewell, Xue Ganom.}

\textit{Life in Zhongyuan without you might be a bit difficult. But I lived just fine without you before anyway.}

\textit{Goodbye the neigh...No, the Greatest Regional-Level Brain.}

\textit{You were my first and last tactician.}

\textit{Though you won't be here anymore, I hope you can live proudly over there.}

\textit{Mhm. And that's the end of the farewell!}

\textit{He's smart, so he'll probably live well on his own.}

\textit{I can always find another tactician if needed.}

\textit{It was nice and convenient having one, that's all.}

Qing looked at her Crutch.

She would be saying goodbye to her too in less than half a month.

"He said to decide on a new name to use. Where was it again? In Sichuan? A name to use there."

Xue Ganom said he would drop off the Crutch in Sichuan.

If all went according to Qing's plan, they wouldn't have time to care about one Second-Grade disciple that ran away. Moreover, who would possibly know she was from the Demonic Cult if she changed her name and washed clean her identity?

He said he would even find a plausible job for her and leave a message at the fifth largest brothel in Sichuan.

It was truly a thorough follow-up worthy of the neighborhood's greatest brain.

"A new name, huh. Have you thought of anything?"

"Yeah."

"What is it?"

"...Xi Xi."

Jian Buxi spoke shyly.

"So, Jian Xixi?"

"No, the name is Xi. The surname is... the same as Junior Sister's."

Qing's eyebrows twitched.

\textit{Wait, this ignorant girl still doesn't know my fucking surname?}

\textit{Come to think of it, maybe I've never told her?}

Reflecting on her own thoughtlessness, Qing finally properly revealed her full name.

"Senior Sister. It's not Xi Menqing, it's Ximen Qing."

"Eh!? It wasn't Munching?"

"Could you please pay a little attention to your pronunciation? It sounds really weird when you say it, Senior Sister."

"Then I'll make my name Ximen Xi... Is that okay?"

Jian Buxi asked, watching Qing's reaction.

\textit{It's not like Ximen is my exclusive surname anyway, and if she wants to use it because she thinks it's pretty, there's no particular reason to stop her.}

\textit{If we're talking about genealogy, we're both unknown orphans who mixed and matched a bunch of names anyway. It's not like the names we have are our actual ones. What does it matter?}

"If that's what Senior Sister wants, then do it."

"Really!? Thanks! Now we really are a family!"

"Oing?"

"Now that we're Sworn Sisters… It feels kind of embarrassing somehow."

Qing blinked her eyes.

\textit{Sworn Sisters?}

Qing was about to ask what on earth that bizarre nonsense meant, but seeing Jian Buxi's radiant expression, she just swallowed her words.

Right. Okay. If it makes you happy, I guess that's fine.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing spent time teaching Jian Buxi the Blissful Maiden Art and Thousand Li Flight.

The Blissful Maiden Art was originally an esoteric doctrine of the Bliss Palace anyway, so Jian Buxi had the right to inherit it.

On top of that, she taught her Thousand Li Flight so that the not-so-kind nor good but lacking Crutch could at least escape in an emergency.

It was a Gold Qinggong specialized in fast and long-distance leaping with good sustainability.

Of course, this inevitably meant that training in the Lustful Immortal Disrobing Dance had to be suspended.

This was a not at all regrettable outcome that Qing had totally not anticipated.

As time passed like this, she finally completed the Heavenly Heart Harmony.

It was on the night she had calmly agreed to meet her Crutch again.

At this point, there was a need to reorganize the Martial Arts Window as well.

A lot of Free Practice Points had accumulated from the night walks, after all.

She raised the Qinggong Techniques Thousand Li Flight and Wind Step to 12 Stars, hence reaching the Grand Star. Moreover, the useful Black Shadow Stealth also reached Grand Star.

After raising various other White and Blue Qinggong Techniques to their maximum of 10 Stars, a subtle tickling sensation arose, as if her body was itching for change.

\textit{Come to think of it, I haven't learned Xue Ganom's legacy, the Supreme Yin Jade Maiden Divine Art, yet.}

\textit{It's a whopping Gold Border, so I should only put it to 3 Stars for now.}

\textit{After all, I should probably be even more numb at the Heavenly Demon Tomb.}

Qing took a deep breath.

"Huuuu."

\textit{For now, let's psych myself up.}

\textit{I have no thoughts.}

\textit{Because I have no thoughts.}

"Urk... ugh... uuurgh..."

Hands that could not be seen kneaded her brain.

Just as Qing's mood was about to plummet into negative numbers, crashing through the bottom of purgatory...

At that moment, the compassionate smile of Buddhism seeped into her brain, providing a sense of ease.

\textit{Great Tranquil Zen Art, is it you again...}

\textit{Come to think of it, aren't the Daoist abilities a bit lacking?}

\textit{There are two Purple Cultivation Techniques, but they haven't really done anything properly.}

\textit{I should have named my character Bodhidharma\footnote{The first Shaolin Abbot} instead of A-Qing.}

\textit{Then I would have started with all the best Buddhist Divine Arts...}

\textit{Mr. Strategy Guide, why did you recommend A-Qing instead of Bodhidharma?}

\textit{Yeah, no. No beef for you. If I ever go back, that ain't on the menu. You don't deserve it.}

\textit{Instead, I'll treat you to some kimchi stew. You hear me?}

\textit{Huh?}

\textit{Ah...}

\textit{I want to eat kimchi stew...}

\textit{I wish I could have a shot of soju with kimchi stew...}

A single tear rolled down Qing's eye.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the language of Zhongyuan, they called food 'ban'.

Here, 'ban' refers to staple foods, including rice.

When you order at a large restaurant, they ask what kind of staple food you would like.

Those from the South ask for 'mi fan', essentially rice.

Those from the East would order dumplings or soup dumplings, while people from the North would order noodles or porridge.

And in the West, with an exception of Sichuan, they were too poor to even enter high-end restaurants, so their staple foods weren't even considered.

Of course, this wasn't absolute, as the characteristic of living in clustered clan villages meant that even within one capital city, staple foods diverged into various preferences.

Under this concept, in Zhongyuan, rice and side dishes were lumped together under the term 'mi fan'.

Side dishes in Zhongyuan were limited to pickles and seasoned vegetables that didn't require cooking and were mere accompaniments to rice.

Everything else was considered a dish.

In the language of Zhongyuan, these were called 'cai' (vegetables/dishes).

In particular, the cuisine of four regions famous for their taste were called the Four Great Cuisines of Zhongyuan.

Chuan cai, Sichuan cuisine. Lu cai, Shandong cuisine,

Huaiyang cai, Jiangsu cuisine. Yue cai, Guangdong cuisine.

Even beyond this, as diverse foods flourished across the vast lands of Zhongyuan, it became a gourmet's paradise leading the world's food culture!

That was how important meals were to the people of Zhongyuan.

No wonder one of their greetings was to ask if you've eaten yet.

Meanwhile, there was another group of people who valued rice just as much as those in Zhongyuan.

A people with a heritage so great and noble that merely thinking of its grand name conjured visions of fluttering illusions. The progeny of humans who had already built the great, gigantic empire of Hwanguk before the great extinction of the dinosaurs (this is a fact depicted in Soo Bahk Do). Who are these descendants, you ask? These descendants who carry the bloodline of such dignified and majestic ancestors?

It was none other than the Korean people!

However, the Korean people had a special affliction.

If they didn't eat Korean food periodically, they would suffer from a serious illness called homesickness.

This was truly a big problem.

If Koreans don't eat Korean food for a long time, they become bedridden with an intense longing for their homeland.

Their whole body loses strength, their mind becomes foggy and can't stand properly, and their motivation and will tumble together in a somersault.

And lo and behold, those were Qing's exact symptoms.

Until now, Qing had somehow managed to get by with pseudo-Korean food, but she had accidentally touched upon forbidden knowledge beyond the veil that she had completely forgotten about until now.

\textit{Kimchi stew...}

\textit{Broth that's so blood-red it's like fresh blood. White and soft tofu that reminds me of brain matter. And then, if I grab a piece of well-stewed kimchi with both hands and cruelly tear it apart...}

"Your complexion does not look good. Are you alright?"

"I'm not okay... I want to go home..."

"There is no need to worry too much. Once we retrieve the Heavenly Demon Spirit, I shall safely send you back. This old man swears on his life."

"Do you even know where my home is? I don't think it would be enough to take me back, even if you added thousands of more lives to your own..."

In fact, at this moment, she truly felt like she could sacrifice thousands of lives if that meant returning home.

\textit{Hmm...?}

\textit{Wouldn't there be a Korea in this world too?}

\textit{Is it Joseon? Goryeo? Anyway, wouldn't there be Korean food?}

\textit{But would those countries be the same ones I know?}

\textit{This was a world where people shot beams from swords.}

\textit{A world where running could surpass the speed of carriages.}

\textit{Perhaps beyond Zhongyuan, there might be nothing but an ocean stretching out.}

\textit{Maybe it's just a pseudo-Earth, an Earth-like planet...}

\textit{I don't know. Who cares anyway.}

Qing slumped in Cui Liweng's arms.

If Qing had been an avid reader of web novels, she might have jumped for joy, thinking 'Ah, so I've finally experienced that transmigration thing that apparently everyone goes through at least once in their life.'

She might have been lost in happy dreams of making lots of money through livestreaming after returning from enthusiastically slicing people up, thus becoming a building owner.

But Qing was just a production worker who barely had time to play games.

She only knew a few memes she had seen in the ocean of information she accessed to find interesting games, and was completely ignorant in this area.

This is why people should read web novels.

It's already a scientifically, philosophically, humanistically, and sociologically proven fact by scholars in various fields that web novels are more helpful than Spanish!

\textit{I don't know. Whatever. I just want to go home.}

Qing just thought listlessly.

If Ximen Surin had seen this state and had a conversation with her, she would have realized that this time, her troublemaker disciple was actually in a state where Inner Demons had entered her mind.

It was because Inner Demons didn't just arise from cruelty or a loss of humanity.

This kind of Inner Demon caused by such intense longing was the type that even the great teachings of the Orthodox Path couldn't prevent.

Because the form of Inner Demons where one lets go of oneself was, in a way, similar to the concepts of Anattā, also known as non-self, in Buddhism and Daoism.

In fact, Inner Demons caused by homesickness were a common and very, very easy to resolve trivial problem.

It was an issue that could be solved by having just one meal with some good people, laughing and chatting in warm company.

However, in this world, there existed a person who could not use such an easy method.

It was already the tenth day of the march towards the Heavenly Demon Tomb.

But for Qing, it was just another day passing by without a trace.
