\chapter{Heavenly Demon Tomb (8)}

Originally, a general does not stand at the front.

It might look good for a general who should be commanding troops to charge bravely while shouting 'Follow me!'

But if he were to get hit by an arrow and fall, the army's morale would instantly shatter and battle tactics would be all but lost without said commander.

So a general standing at the front was purely a decision made to fulfill a selfish desire, not a virtue at all.

Unless it was a situation where risking one's life was necessary.

Strictly speaking, there was no reason for the Alleged Supreme to personally go on this expedition.

He could have just sat regally on his high throne and received the Heavenly Demon Spirit brought to him by his subordinates.

In fact, the current Supreme was practically a figurehead who was not even invited to meetings run by the Demonic Cult leaders.

It would be strange for such an Alleged Supreme to take up a spot on this potentially dangerous Heavenly Demon Spirit expedition.

Yet the Demonic Cult's Supreme was here.

This was because the Heavenly Demon Spirit was a Divine Relic of the cult that humans dared not transport. That those unqualified must not touch.

It was an object the Supreme had to personally acquire.

And as a result, Qing, who coveted such a possession, paid the price.

As if the ground had suddenly given way, the dizzying sensation of falling, pulled by gravity, engulfed her entire soul.

Qing's consciousness faded.

Meanwhile.

Qing's body was also suffering in its own way.

From the Heavenly Demon Spirit that had burrowed halfway into her palm, a pungent and heavy Demonic Qi exploded outwards.

Heaven-Shattering Demonic Qi.

It was a crystallization of malice formed by the Demon God Angra Mainyu, who had condensed all the despair in the world.

The Demonic Qi devoured Qing's body and spread in all directions, swirling and whirling around.

Thus, in the center of the tomb chamber, a majestic vortex of darkness shaped like the universe formed.

Seeing this, Zhi Shengzhu shook his head.

He had expected that she would eventually cause big trouble from the moment she split the heads of Divine Cult officials during transport.

But he didn't think she'd be so foolish as to not even know she would die.

Heaven-Shattering Demonic Qi was an energy humans could not handle.

Even those with bloodlines that carried the Demonic must have their meridians nourished through special procedures from a young age, and cultivate the basic arts of the Divine Veins to barely become vessels capable of holding the Heavenly Demon Spirit.

If someone unqualified tried to contain the Heaven-Shattering Demonic Qi, their body, unable to withstand the rough Demonic Qi that was evil incarnate, would shatter into pieces and burst.

The Demonic Qi that lost its vessel would return to the Heavenly Demon Spirit, making it nothing but a meaningless, stupid death.

As Zhi Shengzhu was clicking his tongue like that...

"No..."

Beside him, Cui Liweng collapsed to the ground.

Zhi Shengzhu shook his head as he watched this scene.

Only the Purple Lightning Demonic Warlord ended up in such a pitiful state.

Zhi Shengzhu had seen Qing's corpse in the Formation.

It was a bloody corpse sprawled out in an illusory place modeled after the Holy Fire Hall.

However, Qing was perfectly alive.

So he thought someone who hated Qing had created an illusion to kill her. Or it was traces of enjoyment by a Demonic Adept with a time fetish.

Now that he thought about it, the owner of that illusion was the Purple Lightning Demonic Warlord himself.

No wonder his attitude towards Qing seemed off.

His mind had become completely sundered inside the Formation.

Qing and his dead daughter had mixed and become one, so his daughter's corpse took on Qing's form.

Thanks to that, he ended up witnessing his daughter's death twice, which was truly a thing of sorrow.

But Cui Liweng had long been a dead man walking.

More important than that, it was time to comfort the pathetic Supreme.

The Supreme was still in a state where he couldn't wake up from the lost illusion.

As Zhi Shengzhu approached the Supreme...

"Oh, the Heavenly Demon!"

"The Heavenly Demon is descending!"

Excited shouts.

Zhi Shengzhu's head whipped around, and soon the young Demonic Brain's eyes widened.

The Demonic Qi that had been swirling in the shape of the universe contracted into a single point for a split second.

It was a space so black it couldn't be seen.

Then, darkness rising in two branches spread its wings towards the sky, burning black like fierce flames and filling the tomb chamber.

Enormous wings. And such wings opened their eyes.

Thousands of eyes lifted their vicious eyelids one by one, in their own order.

Each eye, small and large and tilted, had its own arbitrary number of pupils.

Some eyes had one pupil, others two, three, or even more.

A woman with wings spread like black walls.

On the wings were thousands of eyes and even more pupils.

The cult members who faced this mythical incarnation of evil pressed their knees to the ground.

A brief moment that felt like eternity passed.

The wings had vanished without a trace.

In the center, a girl took her first human breath.

The Second Coming of the Heavenly Demon.

It was the moment when the Divine Cult's long-cherished wish came true.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When she opened her eyes, it was already dark around her.

Qing jumped up from her seat in surprise.

"That's right! The Heavenly Demon Spirit!"

With a scraping sound, the chair fell over backwards with a crash.

Qing turned her head to look around, then froze when she saw the five-legged chair with wheels.

\textit{Wait a minute...}

Qing looked around.

It was a dim room with blackout curtains blocking all light, illuminated only by the faint glow of a monitor.

The feeling was unfamiliar yet strange, but at the same time, it was an incredibly familiar scene.

Qing felt along the wall and turned on the light.

It was an almost unconscious action.

The LED light instantly drove away the darkness.

Next to the sink was a 138L refrigerator.

Qing reflexively opened the fridge and naturally pulled out a can of beer.

With a click, she opened the lid and put it to her lips. The ice-cold beer scraped down her throat.

"Ahh. So cold. Whew."

The cold beer dropped down into her empty stomach.

Only then did her dazed mind clear up.

Qing burst out laughing.

\textit{What kind of crazy dream was that?}

\textit{Going into a game? Da fok?}

Qing checked the clock first.

It was 10:23 PM.

\textit{Wait a minute.}

\textit{Was I on night shift or day shift?}

The matter of a day or night shift was a major issue.

It was related to sleep time. As such, knowing it was crucial; the wisdom of production workers long gone and forever remaining urged them to maintain their biorhythm for even a few days.

If it was day shift, she should sleep now, and if it was night shift, she should stay up all night and sleep in the morning.

But she couldn't remember her work schedule at all.

\textit{Of course I wouldn't. That was years ago.}

\textit{No, wait what? Years? That was just in a dream. The fuck am I saying.}

\textit{But it really feels like years have passed.}

Qing frowned and thought for a long time.

But she still couldn't remember anything.

With no other choice, Qing scanned the desk.

She picked up the familiar smartphone and unconsciously drew an unfamiliar pattern.

She must have touched something wrong, because as soon as it unlocked, the camera app opened.

The face of a pretty girl reflected on the screen.

"Huh?"

Qing looked at the smartphone screen in surprise.

A chunk of hair above her right ear had come loose and was fluttering.

Qing skillfully untied her hair and tied it back up.

After doing so, she felt strange...

-A woman's body? Women aren't born with Divine Veins, though?

It was a sudden voice.

Qing's head whipped around.

It was a beautiful voice coming from the speakers.

The screen showed a scene from the game.

A beautiful girl drawn in an elegant style was reflected, and in the letterbox at the bottom, the previous dialogue was being erased as new text appeared.

Qing read the text in the letterbox.

\begin{quote}
[The Heavenly Demon frowned and muttered.

But that was only for a moment.

The Heavenly Demon couldn't help but exclaim in admiration.]
\end{quote}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"A woman's body? Women are not supposed to be born with Divine Veins, though?"

The Heavenly Demon frowned and muttered.

Perhaps due to the heavy weight hanging on her chest, her shoulders felt stiff. As a result, just the act of standing felt awkward and uncomfortable.

She had lived dozens of lives, but had never been in a woman's body before.

But that was only for a moment.

As the Heavenly Demon observed this body, she couldn't help but exclaim in admiration.

The muscles seemed to be woven from steel, capable of lifting mountains, and the tendons were tough yet flexible, far surpassing the limits of humans the Heavenly Demon knew.

And the vastness of the dantian was more marvelous than any body she had experienced before, to a level that could hardly be called human.

None of the previous bodies had been able to fully contain the Heaven-Shattering Demonic Qi.

And that was precisely why the Heavenly Demon couldn't stay on earth for long after descending.

But what about this body?

It could fully contain the Heaven-Shattering Demonic Qi and still had room to spare.

The Heavenly Demon frowned.

There was True Qi hiding in the Upper Dantian, avoiding the Heaven-Shattering Demonic Qi swirling in the Lower Dantian.

And not just one, but several.

True Qis that should clash as opposites, not unified in Yin and Yang, were strangely clustered tightly together in a corner of the Upper Dantian.

It was as if they were guarding something.

But their actions weren't particularly important.

The Heavenly Demon quickly dismissed it and fully admired the body.

"What does it matter if it is a woman's body? I quite like this body. To think that you would only be at the Peak Realm with such a physique. You must have been quite lacking in talent, hm?"

It was a quiet place where dozens of cult members knelt in the tomb chamber, not daring to even make a sound of breathing.

Breaking this silence, creaking and grinding sounds of bones twisting began to flow.

The sound was coming from the Heavenly Demon's body.

As bones settled into place and muscles reattached, the skin writhed and bulged.

This was called Overhaul Rebirth.

By literally changing bones to take the most perfect form, it was a phenomenon where a body that had reached the Transcendent Realm was reassembled to transform into the best possible form.

In other words, it could be called the optimization of the flesh.

The Heavenly Demon continued walking even during this Overhaul Rebirth.

It was truly an amazing feat.

Anyone else would have been defenseless during the moment of Overhaul Rebirth.

It was a process where all joints dislocated, bones grew or were shaved down, and muscles loosened then compressed and reattached.

It was something experienced only once in a lifetime after reaching the Transcendent Realm.

Along with the pain, one couldn't help but lose their mind in confusion at the strange sensation of the body being reassembled.

But the Heavenly Demon had experienced this enough to be familiar with it.

To the extent that she could walk without staggering even as the Overhaul Rebirth took place.

When the Heavenly Demon finally finished reassembling into a woman's form, a peerless beauty appeared, as if even darkness would be ashamed and draw back its black curtains.

"Demonic Brain, are you there? Who is the Demonic Brain of this generation?"

"The Heavenly Demon has descended, all demons bow down. This lowly one is Zhi Shengzhu. I greet the owner of this soul, as well as the future."

Zhi Shengzhu stepped forward and bowed his head respectfully.

The Heavenly Demon extended her white, slender fingers.

The beautiful hand stroked Zhi Shengzhu's head.

"Oh my. Such a young Demonic Brain. This is the first time I have had such a young Demonic Brain in all my long lives. This means I shall be keeping you by my side for a long time. That pleases me even more. I look forward to working with you."

The Heavenly Demon's words were gentle and loving.

It was the words of the Heavenly Demon Supreme, who was a living god, as well as the long history of the Divine Cult itself.

"Yes, o' Heavenly Demon Supreme."

Zhi Shengzhu's voice trembled with emotion.

That's when it happened.

"Heavenly Demon Supreme! There is a body here! A proper body for you to take!"

A voice dared to ring out without permission.

At the same time, an old man sprang up.

He grabbed the Supreme's nape and slammed her to the ground, then knelt on top of her, pressing her down. And as if that wasn't enough, he also irreverently opened his mouth without even asking permission to speak.