\chapter{Coming Soon (1)}

"Wow, it's been a while since I took a walk with my brother. Why don't we do this more often? You should link arms with me first, given the affection I've raised you with."

Peng Chaolei, who had returned after going outside the city and riding in a prepared carriage, looked very satisfied.

To Peng Chaolei, Peng Daesan was more than a brother but less than a child, leaning heavily towards the son side as an adopted younger brother.

"Chaolei, are you okay?"

"Of course. I got to walk arm-in-arm with my stiff-as-a-board brothe for the first time. I think I can let go of our grown-up Daesan now. I don't know when he got so big and became so blunt and not cute. Hmm. Well, he wasn't particularly cute even when he was young."

Peng Chaolei made Peng Daesan's eyebrows twitch with a joke mixed with sincerity.

But since it was all true, he had no face to refute and just twitched his eyebrows.

Whether his attitude was stiff, whether it was the first time linking arms, whether he was blunt and not cute, whether it was the same when he was young - all items were true without any lies.

"San, you should be nicer to Chaolei too. Where else in the world is there such a sister?"

"Indeed, there's no one but our Qing'er. I should bring in such a child, no, sister. Why don't you become my sister instead, Qing'er?"

'Sister-in-law' is a formal term used in Zhongyuan for a woman to call her younger brother's wife, and in close relationships, they just called them 'sister.'

It was Peng Chaolei's subtle move to casually include her as family, but Qing was completely ignorant of these subtle relationship establishments among women.

This is exactly the fearsome aspect of women.

Peng Chaolei would now subtly change her form of address to 'sister', and eventually do so even in official settings, trying to link them together for all to see and hear.

Peng Daesan, feeling uncomfortable, changed the subject.

"Ahem, anyway, I'm thinking of leaving for Kaifeng tonight."

"Tonight? When?"

"I plan to set out around the Ox Hour."

The Ox Hour is 2 AM for Qing.

The twelve earthly branches are attached to time in the order of Rat, Ox, Tiger, Rabbit, Dragon, Snake, Horse, Goat, Monkey, Rooster, Dog, Pig, so it's not difficult - the middle of the first, Rat Hour, is shortened to midnight, and then it's two hours each after that.

For reference, noon is also the middle of the Horse Hour, but why it's reversed front and back has something to do with the principles of yin and yang, ultimately just needlessly breaking uniformity, showing the level of Chinese standards.

"Oh? The Ox Hour? Why are you leaving in the middle of the night?"

"I can't stand seeing those beggars anymore. Somehow, I'm getting more and more put off."

"I guess so. You always have it tough. Then I'll see you in Kaifeng. You know Zhuge and Lan-Ah, right? Tell them they're doing well and say hello."

At this, Peng Daesan's eyebrow twitched.

"What do you mean? Are you not coming?"

"Me? I was planning to rest and go slowly. Was I supposed to go too? Then who else is going with you?"

"Well."

Peng Daesan flinched as he was about to continue.

He was about to say of course we're going together, who else would I go with, but when he tried to say it out loud, it sounded very strange.

"Chaolei, is Chaolei going too?"

"Me? It would be nice to go together, but shouldn't one child stay behind to host the guests? If both children sneak off completely, what would the Murong and Cao clans think? They'd gossip that we sent them away because we didn't want to see the children getting along."

"Huh. Then, just the two of you? Is that it, San?"

Peng Daesan felt a serious unfairness.

Qing treated him without any pretense, just like a same-sex family member, even last night she just told him to turn around and then casually threw off her clothes and wiped her body.

And that while saying all sorts of things.

But when he actually brings it up, she says something like 'What, just the two of us?'

\textit{Did she decide to be a woman only when it's convenient for her?}

"What's wrong? Is there a problem?"

"No, if it was tomorrow or the day after, I wouldn't mind, but suddenly today is a bit… Can't we go tomorrow? Ah, and don't say things like it's already tomorrow since it's past midnight."

Of course, Qing had no particular thoughts.

She just didn't want to rush ahead of a comfortable schedule.

At this, Peng Daesan's energy drained completely.

\textit{Is she just wanting to be lazy?}

But then again, somehow that makes his insides boil and burn.

"You're not doing anything but lounging around anyway."

"No, I was thinking of visiting A-Jun's place once."

"A-Jun? Who's that?"

"Ah. Murong Jun, there's this little kid. I should tease him when I have something to tease about."

Qing smiled mischievously.

At this, Peng Daesan's eyebrows twitched.

"If we delay any longer, someone might become more annoying. There's that Sword Flower woman, Brother Cao, and his sister too. I'm going, so either follow or decide if you're going to abandon your friend and visit that Murong clan kid."

"Huh? What's with that either-or? I didn't think you had such a childish side- oh? No, you were completely childish from the start. That's right."

Come to think of it, he was just short-spoken and put on airs, but wasn't he blatantly childish from when they first met?

Saying 'Hit me, hit me, can you hit me?', trying so hard to get hit that she gave him one.

"What, childish? What nonsense from that open mouth."

"Usually, people who are guilty burst out like that, you know? Haah. What can I do? I'll have to go with our San who has no friends besides me. A-Jun seems like he'd have a lot of friends, so even without me…"

"Ha, no friends? Me?"

"Yes. What friends do you have? Name them."

"Hmph, you think I can't name them if asked? First."

Peng Daesan paused.

\textit{First what?}

\textit{That Sword Lunatic guy? No.}

\textit{The Zhuge clan is just clingy and calls everyone brother or sister, but there's no particular personal friendship.}

\textit{Brother Cao is terrible. Brother Changbin and Brother Hwangbo are too much like older brothers to call friends.}

And with the other rising stars of the Dragon-Phoenix Assembly, they're just acquaintances who meet to eat, not friends he could call without formality.

\textit{Have I, had no friends?}

At this sudden realization, Peng Daesan froze.

"See. Only the great Ximen Qing."

"Kuk, then what about your friends-"

"What, shall I name them? Can you handle it?"

Qing pulled up one corner of her mouth into an insufferably crooked smile.

"Forget it. I'll go alone, so go meet all those great friends of yours."

"What, are you sulking?"

"Ha. Don't talk nonsense."

Qing's eyes narrowed.

\textit{This kid, he's really sulking.}

"Hey, what's this. San. The man Ximen Qing doesn't betray loyalty like that, you know? How could I let a friend set off on a lonely journey? Getting upset over a little teasing."

"I'm not upset."

"Come on, really? You really weren't upset? Wasn't this friend upset that I said I wouldn't go with you?"

Qing asked, poking Peng Daesan's side with her elbow.

And then Peng Daesan burst out again.

"No, stop! How can a woman be so familiar, can't you have some common sense?"

"Come on, what's wrong between friends?"

Seeing the two bickering, Peng Chaolei left with a smile, quietly slipping away.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The martial arts clans of Zhongyuan are as diverse as their surnames because originally, local influential families who were somewhat powerful changed their names to sound more impressive.

Among them, the most famous five are the Five Great Clans, and to match numbers with the Nine Sects One Union, they added five more to create the Ten Great Clans.

Among them was the Jin Prefecture Yun Clan, but it no longer exists.

(We should hear Yun Yuanling's opinion too)

With one vacancy, it needed to be filled, and for local influential families who prided themselves on being close to the Five Great Clans if not quite at their level, there was no better opportunity.

And among them, there was one clan with a very unique surname.

The Gong Clan.

The Gong surname was that of humanity's first emperor and the greatest sage of China, and this clan claimed to be descendants of that great primordial ancestor Emperor Gong Xuanyuan.

It was a claim because the truth couldn't be verified.

However, this claim could also be related to treason, so after being severely punished once long ago, they were forced to change their surname, dropping the 'Sun' from 'Gongsun' and leaving only 'Gong.'

Still, unable to give up the clan's identity of 'Gongsun', they used a unique workaround of using 'Sun' as the first character of every clan member's given name and making names three characters long.

Thus, the name 'Gong Clan' that somehow maintained 'Gongsun' contained such pain and the unyielding integrity of the clan's irreplaceable identity.

And so, the current clan leader Gong Sondaewol, Son Daewol of the Gong clan, said:

"Finally, our clan's long-cherished wish is within reach. With the government being a mere figurehead, once we're listed among the Ten Great Clans and tied together as one, who could stop us from reverting to the great ancestor's surname?"

The Ten Great Clans of Zhongyuan are not just the top ten clans ranked from above.

It's a network of you, me, us all tightly bound together, truly the greatest and most magnificent guanxi under heaven.

It was their long-cherished wish and ambition to change Gong back to Gongson, relying on the power of that fence.

"For this, your roles are important. You must show an overwhelming performance at the Hidden Dragon Secret Competition. And also, you must form ties with influential women from the Ten Great Clans, no, should I say Nine Clans now? Or the Five Great Clans or Nine Sects One Union to secure allies for our clan."

"Yes, Father. Don't worry."

"Yes…"

"Good. I'll trust in you."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Do we really have to do this? Can't we just ride out in a carriage?"

Qing, dressed as a servant, said.

Peng Daesan, also in servant attire, answered.

"You're underestimating those persistent characters too much."

And so, in the dead of night, a little past the Ox Hour, a man and woman slipped out through a side door of the Changyuan Daoist Temple under cover of darkness.

With their faces lowered, looking only at the ground and taking small steps, they were clearly servants to anyone who saw them.

As they brushed past and secretly looked around, Qing understood Peng Daesan's words.

\textit{Wow, really. Persistent women.}

It was like this, for example.

On a moonlit night.

Two people who happened to meet while strolling the night streets, unable to sleep.

Night is bewitching, and unlike under the bright sun, hidden intimate desires peek out under the darkness. (Like 3 AM texts)

And so, what would a man and woman drunk on moonlight do in the darkness?

Eyes meet, lips meet, and with only the stomach left among body parts, maybe match stomachs too…

In fact, they could be called more clever women.

Swarming around in broad daylight would just make them one of countless flowers, but meeting at night would allow them to remain as a single woman in their entirety.

With such pure, or rather brain-pure imagination, they loitered in front of the main gate all night long, leaving the Jade Qilin without freedom day or night.

And so, Qing collapsed onto the luxurious, soft seat of the carriage waiting at the stable, burying her back.

"If it's annoying, why don't you wear a face veil like me? Gramps gave it to me, saying all sorts of bastards would cling to me."

"What man wears a face veil?"

"Then at least pull that bamboo hat down low. Can they recognize you just by seeing your lower face?"

"Ha. I've done nothing wrong, so why should I hide? In your eyes, have I ever avoided those characters out of concern?"

Whether it was on the road to Luoyang attached to a caravan, or traveling as a trio with Sword Friends, the Jade Qilin had never particularly hidden from pursuers.

He had never made excuses to eat in private rooms or go somewhere to avoid them.

Then suddenly, a thought occurred.

"Huh? Then, now? Aren't you avoiding them?"

"Hmm?"

Peng Daesan's eyebrow twitched again.

But this time, the movement of his eyebrow wasn't a sign of discomfort, but rather an "Oh?" meaning.

"That's…"

Peng Daesan tried to make an excuse but closed his mouth.

Even he thought it was true that he was avoiding them.

So he fell into confusion.

\textit{Why did I sneak out in the middle of the night like someone who's not above board?}

\textit{It's not like those characters have been acting like this for just a day or two, there must have been something particularly irritating to make me do this.}

But no matter how much he thought about it, nothing particular came to mind, so he could only feel a tickling in his frustrated insides.

And then, Snore. Ssaek.

Somehow familiar snoring sounds, cute sounds like the black dog raised in the clan makes when sleeping, woke Peng Daesan from his pondering.

It was coming from Qing, who had fallen asleep lying on the carriage seat.

"What is this."

Peng Daesan was at a loss for words at the sight of the sleeping beauty.

One hand was casually placed on her eyes with her forearm, while the other hand hung limply outside the seat.

Meanwhile, one leg was bent high with the knee resting on the backrest, while the other leg was hanging off the seat with the sole of her foot on the floor.

It was a terrible display that would incur Ximen Surin's extreme anger and nuclear bombing punishment if she saw it.

They say when you're dumbfounded, words don't come out, and this happened frequently in front of Qing.

"Haah."

The speechless Peng Daesan just let out a deep sigh.