\chapter{Coming Soon (6)}

As they reached the top floor, it suddenly became quiet and gazes stabbed towards them.

Soon it returned to its original atmosphere as if nothing had happened, but during that moment of silence, Qing provided a lot of information to the Phoenixes.

The women exchanged glances and gauged her 'rank' based on the information they gathered.

'What's this, her face is covered.'

'She's using quite a good face veil. Is it Bulagasa silk? It's totally luxury.'

'But only the face veil is luxury? She must not have much confidence in her face.'

'Look at the shape of that body. Did everything she ate just spread out up and down?'

'Ha. With breasts like that, they wouldn't show even with clothes on, and what's with those hips, skirts wouldn't even fit.'

'I'm not saying this out of envy, no I'm not crying.'

'But, martial attire? The fabric is good quality but not quite high-end.'

'She doesn't seem to care much about adornment.'

'The upper garment is a long jacket to the knees, with a crossed collar covering high to avoid exposing the collarbone, isn't it suffocating just to look at?'

'She's from a martial sect rather than a clan, and among them, probably a Daoist sect.'

'Why is she carrying two swords, and she even came in wearing a flute prominently as if she knows how to play it.'

'But if you're going to use a flute, use a good one, is that a short staff or a flute?'

'Moreover, if you came, you should at least greet people, why are you just awkwardly looking around?'

The conclusion they reached was that she was an ugly country bumpkin who came up from some local Daoist temple.

The women's level of vigilance instantly dropped to the bottom.

If you were to look at the scene in the tower frame by frame, you might notice an interesting phenomenon.

The gazes that had all focused on Qing at once returned to several women who had already taken their seats in the hall.

And those women who received the gazes glanced at each other, checking each other's reactions.

The women receiving the gazes were the faction leaders, the heads of cliques.

And this was the bidding process of the clique leaders.

'Who wants to take that country bumpkin?'

'She doesn't seem worth much. I'll pass.'

'She seems to be in the female martial artist category.'

'Taking her wouldn't be beneficial and she has no sense. Ah, what a waste.'

Since no woman asked who she was first, it meant that no faction was extending a hand after her failed attempt to appeal her charm upon entering.

Then there were two choices for a woman to make, and one choice for a martial artist to make.

If Qing were a woman skilled in socializing, she would have approached the faction leader of her choice, introduced herself first, flashed a smile, and wagged her tail saying 'I want to be friends with you.'

Or she could have drooped her shoulders with a disappointed look, thinking her debut at the Phoenix Association had completely failed, and headed towards the seat for rejects in one corner.

(There's always a gloomy 'reject zone' in one corner of the Phoenix Association gatherings)

And if she were a martial artist, she would either be ignorant of women's power struggles or know but not care, and head towards the separate 'female martial artist zone.'

This was a place for female martial artists who weren't interested in complicated power struggles, those closer to martial artists than women.

Would Qing understand these complex inner workings?

She just looked around the gathering, thinking 'Wasn't Miss Gong supposed to be here?', and her simple impression was:

\textit{Wow, they're all dressed so gorgeously.}

That's when Tang Lan-Ah came up the stairs.

"Oh, Qing'er, I told you to wait a moment but you already came up. Here, put on this scarf, it's one I cherish, it's Sichuan brocade."

Tang Lan-Ah made a show of personally draping the scarf over Qing's forearms and adjusting its hang.

A scarf refers to a wide and long piece of cloth, usually draped over both forearms and hanging long down the back and sides.

The long cloth of unknown purpose that often appears in fairy paintings is this scarf.

"I don't understand why people wear scarves. Isn't it just uncomfortable? You can't even lower your arms when wearing this."

When wearing a scarf, your arms basically end up in an awkward jump rope position.

If not, it would drag on the ground.

"It's because it's pretty. Ah, it's beautiful."

At this, tension circled the hall again.

'Isn't that the Poison Flower? It is the Poison Flower.'

'Damn, the queen bitch is here. Why did that unlucky one stuck in Sichuan come all the way to Kaifeng?'

'The Poison Flower lent her own item? Did she go crazy from mishandling poison?'

At this, Tang Lan-Ah shot glances here and there as if to show off.

Her gazes reached the clique leaders, and they all exchanged glances while snickering.

'Is that playing servant? The great Tang Lan-Ah is clinging to such a rustic ugly woman?'

'Moreover, she seems to know nothing about this side? What's she doing bringing someone who knows nothing?'

That's when it happened.

A tiny thing came running with high-pitched screams like a bird.

"Sister! Gege sister!"

"Oh, isn't it Xiang'er. Our Xiang'er was here?"

Qing lifted Zhuge Xiang up, spun her around twice, then hugged her close.

The seven-year-old little lady let out a clear, pleasant child's laugh, giggling happily.

"Ah, Gege sister, did you see our brother? I saw him after a long time but he didn't play with Xiang'er, it's too much."

"Your brother is over there where the men gather. He'll probably go home today, so ask him to play with you to make up for the missed time."

"Heheh, okay."

And when Qing tried to put the child down, Zhuge Xiang hung onto Qing's neck like she was clinging to a tree, with no intention of letting go.

Qing chuckled and hugged Zhuge Xiang again.

At this sight, the women raised their level of vigilance again.

'She was a woman followed by the Zhuge Clan's darling, putting the Poison Flower below her.'

'She wasn't just a country bumpkin.'

That's when a pretty beauty somewhere in the middle spoke with a bright smile.

"Hey, Poison Flower. A new Phoenix has arrived, aren't you going to introduce her?"

So Qing looked at that woman.

\textit{Wow, what? Gulp. How can she wear clothes like that?}

Seeing it directly, the impact is incredible.

It was a trend called 'thin-transparent-exposed.'

Thin means thin, transparent means see-through, and exposed means revealing, encompassing all three in one outfit.

It involves wrapping a sash around the ribs to lift the breasts up, then wearing a very long skirt.

Add a see-through gauze vest on top and the thin-transparent-exposed look is complete.

Many poets were inspired by this desirable attire and wrote poetry, with famous lines like:

'White snow piles up on the front chest.'

'The exposed chest is white as snow.'

'The revealed chest is like snow reflecting the sky.'

They all compare breasts to snow, not because of plagiarism, but because snow-white skin is considered beautiful.

Meanwhile, how much of the upper chest was exposed depended on the individual's confidence, wealth, and level of power.

The higher all three were, the lower and more area was revealed.

And the confidence of the woman who spoke to her was at the maximum level, dangerously close to the edge.

Qing struggled to correct her instinctively drawn gaze and said:

"Ah. Hello everyone. I'm Ximen Qing, an outer disciple of the Divine Maiden Sect. I'm lacking, but I've studied under Master Ximen Surin."

"Grand Matron!" "Zenith Among Women!" "Grand Matron!"

\textit{This doesn't distinguish between men and women, huh.}

\textit{And this sharp chorus again.}

\textit{It seems like there's a rough one, two, fire rhythm, and as long as they shout simultaneously, it doesn't matter if the content is slightly different.}

\textit{I should try joining in instead of standing alone stupidly if I get the chance later.}

Qing inwardly resolved.

And that opportunity came right away.

"So you're Miss Ximen. I'm Chen Sui\footnote{陳歲. Jin Seol (진설) in the original text}. You must have heard my name?"

And then Chen Sui made an expression as if waiting for something, and Qing sensed it.

\textit{Ah. This is the moment I should shout now!}

\textit{Um, so, Chen Sui um.}

\textit{Who are you?}

Qing realized a serious error.

Shouldn't you know something to shout?

That's when Zhuge Xiang blew her hot child's breath into Qing's ear through the face veil.

"She's Miss Chen Sui of the Guangdong Jin Clan. She's in charge of the Blooming White Lily among the Five Flowers of Wulin."

"Blooming White Lily!"

Qing cheated and copied the correct answer.

Although the timing was quite late, Chen Sui nodded with a proud expression.

In Chinese poetry, there's a line that goes: 'Sitting like a peony, standing like a peony, walking like a lily.'

This describes a beauty, and among them, the lily is known as the flower of flowers for its strong fragrance and pure beauty.

Chen Sui, the Blooming White Lily, was just like that.

For reference, Sword Flower Murong Zhuxi claimed that they just called her Lily because Chen Sui had no special skills.

She didn't stop there, showing hostility by saying that because she had nothing else to show off, she always went around with her chest exposed, clearly aiming to be the Pervert Flower or Slut Flower.

It wasn't entirely baseless.

There's the Poison Flower who uses poison, the Sword Flower who's surprisingly serious about swords. The Wise Flower who's smart and the Snow Flower who uses ice arts.

Although all five beauties are beautiful enough to be called the Five Flowers of Zhongyuan, Chen Sui doesn't have any notable characteristics or special skills to speak of.

Of course, she claims it's because she's the most beautiful.

"My, our Xiang'er is just like Zhuge Liang? As expected of the Zhuge bloodline. So reliable."

"Heheh."

Qing rubbed cheeks with the child through the thin face veil.

Zhuge Xiang burst into happy laughter, and Tang Lan-Ah lit up with jealousy at the sight.

It was the ugly image of a villainess being jealous of a seven-year-old child.

Chen Sui gently tested the waters and checked the situation.

Even if there are differences in distribution, clans aren't as strict as Daoist or Buddhist sects anyway.

"Let's see. We should prepare a seat for Miss Ximen. Where is there an empty seat…"

Just as even cold water has its levels, the Phoenix Association banquet also has upper and lower seats.

This doesn't officially exist so no one explains it, but if you violate it, you'll immediately face five hundred times the gossip and subtle ostracism.

So you had to figure it out on your own, read the room, and find your place well.

And Chen Sui's ploy towards Qing was exactly this: a scheme to relegate her to the lowest of the low seats.

It's an evil strategy with no escape route - if you don't know, you'll be laughed at for being stuck in the lowest seat, and if you do know, you can't refuse from your first banquet appearance and have to accept it with seething anger.

She doesn't particularly have bad feelings, but she can't help it since that Tang Lan-Ah bitch is sticking to her.

The humiliation and insults she suffered because that dog-like woman neutralizing poison are still vivid.

In the end, it was because of Tang Lan-Ah.

And just as Chen Sui was about to make her move!

"Ah. It's fine. I just stopped by because I heard Miss Gong was here. I plan to just have a brief private conversation and leave."

"Ah. I see. But since we've met like this…"

"I'm sorry too. But I can't spend much time because I have companions, so please understand."

Chen Sui's smiling face became a bit awkward.

That's because she was thinking something else inside.

‘Right, so you're trying to slip away like this? Okay, fine, companions. What kind of companions could you have?'

She thinks she's going to look around for men from the Nine Great Sects based on her background.

Well, I wonder if there's any man who understands women's power struggles.

"Then will you please join tomorrow's gathering? I'd like to talk with you, and since all of the Dragon-Phoenix Assembly will gather in one place tomorrow, it would be good if your companions join too, right?"

"Ah. Is that so? Will there be a lot of food?"

"Of course, rare dishes from all over Zhongyuan will be gathered in one place."

Qing's eyes flashed.

\textit{Well then, I can't miss that.}

"Excuse me, is Miss Gong here? Ah. There you are. Now, Xiang'er. I have something to discuss privately, so the swinging is over now."

"Swinging? Is that a dialect? But I can understand what it means right away…"

Qing patted Tang Lan-Ah's shoulder, telling her to at least exchange greetings with some familiar faces.

At this, Tang Lan-Ah walked out boldly, then pushed aside the woman next to Chen Sui and took her place instead.

Qing approached Gong Sun-Yaoyi directly, assuming the Five Flowers of Wulin knew each other.

As it happened, the seat where Gong Sun-Yaoyi was sitting was the very lowest seat, but Qing didn't know anyway.

Of course, even if she had known, she wouldn't have cared, but that doesn't excuse her ignorance