\chapter{Coming Soon (3)}

As soon as the scream was heard, nearby onlookers quickly ran away, only to be blocked by a wall of people in front and turn back with shining eyes.

In Zhongyuan where knife fights are common, people first run away to avoid getting involved, then turn back to become spectators when they feel they're at a safe distance.

After all, you can't call yourself a Zhongyuan person if you avoid watching fights.

In the quickly formed clearing, Qing stood firmly holding the man's wrist.

"Aagh!"

"Look at those bad hands. Those who steal others' belongings have their wrists cut off. The law is strict, where do you think- Hmm, is that right?"

She said it smoothly as if it came naturally to her mouth, but she wasn't sure if that was really the law in Zhongyuan.

So Qing looked at Peng Daesan for confirmation.

Peng Daesan shook his head.

"There's no such law."

"Ah. Oh no. You should have told me a little earlier. It's already half cut off."

When Qing let go of her hand, the man kept screaming with his tattered wrist.

He wanted to grasp his wrist, but the searing pain when touched prevented him from doing so, leaving him just stamping his feet, which looked a bit pitiful.

\textit{I should have just cleanly cut it off.}

\textit{Unnecessarily grinding the bone to powder, now the lower part of the wrist is just hanging by skin and tendons.}

Qing expressed this regret in her words.

"Won't you shut up? If it hurts that much, I could just cut it off completely?"

"Wh-what is this! Why, why!"

"That's what happens when you grope other people's bags. Hey, miss over there? I saw this bastard rummaging through your bag. You should be careful."

"Don't be ridiculous, I never-"

"Be quiet."

Whack!! The Fushen-di that had appeared out of nowhere struck the pickpocket's crown.

With the majesty of a proactive and revolutionary radioactive ten-thousand-year cold iron bombing, the pickpocket's eyeballs rolled back somewhere inside his eye sockets.

"Now, let's see."

Qing skillfully searched the corpse (not really) and found a pouch tied at his waist.

Inside the pouch was an elaborate hair ornament decorated with modest pearls and red jade.

It was the item Qing had seen him stealing.

"This is your item, right miss? I saw this guy taking it out."

However, the woman's reaction was strange.

Her pupils were shaking severely, her complexion had turned pale white, yet she couldn't take her eyes off the hair ornament, just staring at it.

"Miss?"

"It-it's not mine."

"Huh? I clearly saw this guy taking it out. Ah, are you perhaps afraid he might do something to you?"

"Ha. Are you trying to insult me? You think I, Gong Sun-Yeye of the Gong Clan, would lie out of fear of future consequences? Is that what you're saying?"

The woman suddenly spoke while grasping her sword hilt, her voice chilling as if she might really draw and swing it.

"That's not it. I clearly saw him stealing it, but you say it's not yours. I was just wondering."

"I-I told you it's not mine. Before being a woman, I'm a martial artist. Aren't such ornaments worn by weak women?"

Indeed, her plain martial attire and face without a trace of makeup, with her hair simply tied up with an uncolored cotton string as her only adornment, didn't match.

Still, she's pretty.

They say a true beauty is beautiful with a bare face.

However, she didn't look like someone who would own such an elaborate hair ornament.

"I must have seen wrong. Strange."

"That ownerless thing, throw it away immediately."

"No, I should find the owner, not throw it away."

"Then do as you please. Anyway, it's not mine, so I'll be going."

And with that, she walked away briskly.

As Qing stood there dumbfounded, Peng Daesan asked.

"Could you have seen wrong?"

"No, I didn't? I clearly saw it. When he took out something so fancy, I thought it must be expensive and precious."

That's when it happened.

The pickpocket suddenly shouted.

"You, you bitch! How dare you do this to an innocent person's arm! The law? Fine, let's go by the law! Do it by the law!"

"Ha. This bastard suddenly got cocky. What did you do right, you thief stealing other people's things? I should have just cracked your head open."

"Oh my! This woman is framing an innocent person! Aagh! My hand! Officer! Officer!"

Qing burst out laughing.

"What's this, a thief calling for officers? Besides, in all my time in Zhongyuan, this is the first time I've seen someone call for officers. San, have you ever seen officers actually working?"

It wasn't a question asked out of curiosity or ignorance.

It was just an extension of mockery.

It was an era where people openly said there were five most lowly professions, and below them were government officials.

At least the five lowly professions tried to earn money, but officials were commoners who enjoyed unearned income without doing anything.

"Well, I have seen it."

"San?"

"The officers here do work."

The corners of Peng Daesan's mouth visible under the bamboo hat formed an annoying smile.

"What? What do they do?"

"In Kaifeng, even officers are respected. Didn't I tell you before? They have a temple enshrining Bao Zheng."

As soon as Peng Daesan finished speaking, soldiers in black official uniforms with large 'Arrest' characters embroidered on them appeared through the crowd of onlookers, surrounding the area and raising their spears.

Qing scanned their faces and realized that none of their Evil Karma exceeded thirty points.

"Damn, it's real."

At that moment, a man wearing similar attire but with a gold-embroidered belt walked out from among the officers.

"What's all this commotion?"

"Sir! I've been wronged! This woman suddenly crushed my wrist and tried to frame me as a thief by threatening me. How can there be such an unjust thing in this world?"

"No, this thief-"

"Enough. Hmm. Why did you harm an innocent person? If you say this man is a thief, do you have evidence to prove it?"

"I clearly saw him stealing this with my own eyes."

"That's a lie! Everyone here heard and saw that this is a treasure I bought after saving money for a long time to give to my wife!"

"No, this bastard is lying every time he opens his mouth-"

"Enough. If you say you saw it with your own eyes, where is the owner who had this item stolen?"

"What? Well…"

Qing trailed off.

The actual owner of the item had gotten angry saying it wasn't hers and left.

What kind of woman is that?

Just because she has a pretty face.

As Qing hesitated, the gold-belted man shook his head.

"I'll arrest you for robbery and assault. If you have any grievances, you can explain the details at the yamen later. Will you accept the rope willingly?"

The 'rope' referred to a thick, red-dyed straw rope used to bind criminals' arms when escorting them.

If the criminal was compliant, only their arms would be tied, but if they resisted violently, they might be dragged along with it around their neck.

In other words, telling them to accept the rope willingly meant to follow quietly if they didn't want to look like that.

Peng Daesan spoke while making a sound as if trying hard not to laugh.

"The Gong Clan isn't hard to find. I'll look for them, so go and wait quietly. Well, even if things go wrong, you'll just get a few lashes anyway."

This was Peng Daesan's very warm comfort to Qing, who had accepted the rope.

Qing gritted her teeth.

\textit{This bastard San, that's why you have no friends.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

His surname is Bao, given name Zheng, courtesy name Xi'ren.

This person called Bao Zheng, or Bao Xi'ren, was a famous prime minister of the past, also renowned for his incorruptible character and impartial attitude.

He was revered as the greatest incorruptible official in Chinese history and respected for generations, and the temple dedicated to him was a sacred place that all officials should visit at least once to emulate his spirit.

This sacred place is destined to be burned down under the guns of the red people in the future, but even after being burned, it remained an incomprehensible mystery that swelled the hearts of the Chinese people.

'How could a government official be incorruptible?' 'Was he mentally ill or disabled?' They wondered.

And so people called him Bao Qingtian.

Qingtian means a clear sky without a single cloud, a nickname meaning that Bao Zheng's rule was as transparent and clean as that.

So was Qing in trouble because of this? Actually, that wasn't the case.

If it wasn't treason, all punishments under the law could be substituted with money.

This was called 'ransom punishment', meaning washing away crimes with money.

Even the death penalty could be replaced with gold nuggets.

This was also why Peng Daesan had thrown a crooked joke at Qing as she was being dragged away with her hands tied.

Anyway, you could just pay money, and for the wealth of a Wulin clan, it wasn't a burdensome price to begin with.

"Your companion has paid the ransom, so you can come out now."

The young man who had brought Qing in, the Kaifeng Prefecture Inspector, said as he opened the prison door.

"What was the verdict? How much did they pay?"

"Five lashes and sixty copper coins."

"Wow, that's really cheap."

It was a very cheap fine for completely disabling someone's wrist.

The investigation concluded that the man was a pickpocket, and moreover, a criminal who should be severely punished for multiple serious crimes, so the verdict took this into account.

Flogging is a light punishment where they whack your buttocks with a sturdy bamboo rod.

For men, they'd strip them down to their underwear and hit their bare buttocks, but they wouldn't go that far for women.

Getting hit five times would just leave five lines on each buttock, ten lines in total.

It was a punishment closer to the humiliation of being beaten in public with spectators gathered than the pain.

"Please restrain yourself in the future. No matter how evil the other party is, if individuals take punishment into their own hands, how can there be law and order in the country?"

"Hmph, is there any law and order anywhere in Zhongyuan besides here? It's so bad that Wulin gangsters are maintaining public order."

Qing, who had been locked up in a cold cell for two nights, answered sharply.

She was angry because the food was too poor, even worse than the cold cell.

By law, prisoners get two meals a day, small in quantity and bad in taste, with no extras allowed.

"Ahem. Not all officials are like that."

The Inspector coughed uncomfortably as he spoke.

Even he felt it was a lame excuse as he said it.

As they came out, Peng Daesan smirked.

"Should I have just let you get beaten?"

"I have sixty coins too, you know? Damn, who was that woman anyway? I helped her for nothing."

If that Gong whatever woman had just told the truth from the start, there would have been no need to be locked up in prison for two days.

Ransom punishment was only possible after the verdict, so it took time for the pickpocket's crime to be revealed.

"Still, you have one hair ornament left. It's a precious ornament with pearls and red jade, not a single fake mixed in. It's more than enough for what you earned in two days."

Peng Daesan said this and tossed the hair ornament up.

Qing caught the hair ornament as it traced an arc and examined it. Well, it's certainly pretty.

Too flashy for Master to wear.

\textit{Maybe I should give it to Changming.}

"Ah. I'm starving to death. Even if they're criminals, how can they make people miserable with food? What kind of meal is that even a dog wouldn't eat?"

"You probably licked the bowl clean."

"Huh, were you watching? You know so accurately. Then why didn't you secretly throw me some dumplings?"

Peng Daesan's Inner Qi was far too weak to scratch Qing's insides, so to speak.

This body is the terrifying chatterbox recognized by none other than the Beastly Sage Zhuge Lixian, a master who couldn't hold back exclamations of 'You argue like a dog!'

Saying someone argues like a dog is a compliment.

It's the highest praise filled with respect that the loser in an argument gives to the winner.

As they returned to the inn chattering like this, what's this?

They say a dog comes when you call its name. The muscle lump Zhuge and Tang Lan-Ah suddenly stood up and came running.
