\chapter{Coming Soon (5)}

Suddenly, the private room became solemn.

After a moment of silence, Qing tilted her head, and everyone offered their own comments.

"It's true that Gong Sun-Yeye woman was rude, but the Gong Clan are people who keep to the right path, so it shouldn't be enough to harm her."

"That's right. Sister, you shouldn't kill or maim her. Even if not for that, there's the Hidden Dragon Secret Competition, ah, you know killing is forbidden in the Hidden Dragon Secret Competition, right?"

"Yeah. Yeah. I'll give you a few untraceable poisons, so do it secretly, secretly. What? Why?"

Qing narrowed her eyes.

"What's this, how do you see me? I'm not asking to do her harm. I just want to return the hair ornament, that's all."

"Is there any need to do that? She denied it was hers, so you won't particularly get any thanks for returning it."

To this, Qing laughed awkwardly and said.

"No, Zhuge just talked about women's underwear earlier."

"Sister. If you say it like that, doesn't it make me look like a strange person? What women's underwear talk?"

"What? Are you saying I lied? You clearly said a woman's underwear was secretly removed without her knowing."

"This is the technique of misleading the truth with facts by editing parts… By removing the subject, it sounds like I did it. As expected, Sister, you're terrifying."

"You know that, yet you've been getting cheeky lately. Anyway, so Zhuge told me that returning the stolen underwear resulted in getting slapped, right?"

"If you're going to do it anyway, could you please add the subject, ‘the Divine Thief'?"

"That's the same thing. Come to think of it, when normal women experience such a thing, I'm not sure if it's possible to not notice, but anyway, wouldn't they pretend not to know rather than slap? Saying, ‘That's not my underwear.'"

Because if they get angry there, it confirms that the underwear is theirs.

At that moment, the woman is no longer an ordinary woman.

She becomes a woman not wearing underwear!

In Qing's opinion, it could be said she's realized the way of comfort, but that sense of liberation and the situation of being exposed in front of others were separate matters.

"So, well. I think I was careless."

"But it's a hair ornament, right? What's the problem with a woman having a hair ornament that she made such a fuss and got you locked up and starved for two days?"

"That's not for me to judge. Let's say, for example, aphrodisiacs were found in San's possession…"

If San experienced the same thing but the stolen item was an aphrodisiac?

Then the women following him would say, 'Wow, I know how to take aphrodisiacs too. I want to drink it all up' while licking their lips.

If it came from Tang Lan-Ah's possession, everyone would just say it's natural because she's from the Tang Clan.

But if aphrodisiacs came from Zhuge's possession?

He'd just be a muscle pervert exercise freak.

They'd point fingers saying he's a beast with the body of a beast, the brain of a sage, and the heart of an animal.

"Sister? Why only this younger brother…"

"Forget it. Everyone's circumstances are different, so San would deny it's his while lowering his voice a lot and shaking his eyebrows up and down, right? Since the person involved feels the shame, I shouldn't judge carelessly."

If it was something like a long phallic model instead of a hair ornament, Qing wouldn't have asked in front of people, 'Which of the gold dick, silver dick, or wooden dick that you stole is yours? This bastard stole it, so pick it out in front of all these market people and take it.'

But for Gong Sun-Yeye, the hair ornament might have been at a similar level of shame as a dick.

Saying the intention was good is no excuse.

Similarly, saying you didn't know doesn't work either.

Anyway, Miss Gong Sun-Yeye had denied it and left in a burst of anger.

Yet her eyes looking at the ornament were quite uneasy, so it might be an item with a story.

"So it's right to return it, yeah."

"Wow, Qing'er, really your heart, wow, how. Let me see your clothes, let me check for sewing marks."

'Heavenly clothes without seams' means clothes of a fairy or comparable craftsmanship.

Tang Lan-Ah said this while hugging Qing tightly, not hiding her truly moved voice.

"Really, Qing'er is too kind. Beautiful heart, beautiful face."

To this blatant praise, Qing answered with an awkward smile.

"Lan-Ah. Isn't the position of your hands a bit strange? Usually when hugging, you don't put strength in your hands, right?"

"No? Since I hugged from the side, it's a very natural arm position? This is how we do it in Sichuan? It's not strange at all?"

"This girl, whenever she gets a chance."

Qing peeled Tang Lan-Ah off.

She tried to cling and not let go, but how could she match Qing in strength?

"So, where is Miss Gongsun?"

"She's staying at the Alliance's guest house."

At that moment, Zhuge Lixian interjected.

"Sister, just in case, it's not Miss Gongsun but Miss Gong."

"Oh? Then is her name Sun-Yeye?"

"That's right. However, it's better to call her Miss Gongsun. Miss Gongsun would prefer that too."

"What's that about?"

And so Zhuge Lixian took a deep breath.

A grand explanation was about to begin.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The biggest flaw in Qing's personality could be said to be her careless and impulsive decisions.

And her greatest strength is her excellent execution ability to move without hesitation once she makes up her mind.

And when you combine these strengths and weaknesses?

The good points all disappear and only the flaws double.

It's also a characteristic of people who stupidly repeat two, three, four times what should be finished in one go.

"Hmm. How about it, San, want to come along? You've covered your face for once. Won't you be discovered if you go?"

"Hmm. Hmm. Hmmm."

Peng Daesan pondered uncharacteristically hard.

Indeed, the few days of going around with his face covered had been a whole new world, to the point where he realized that Zhongyuan people live so comfortably while he alone was uncomfortable.

\textit{So I should enjoy it for a few more days.}

Peng Daesan came to a conclusion.

"I'll go together. Don't you not know anyone at the Dragon-Phoenix Assembly meeting?"

Peng Daesan was inwardly flustered.

He had meant to stay separate, but the answer came out without him realizing.

"It's not just a day or two, you've looked quite relaxed all this time. Zhuge and Lan-Ah are there too, so you don't have to force yourself."

"Forget it. As someone said, I'm a man with no friends, so I'll try to make some this time. The only one I have isn't reliable, so it feels like looking after a child playing by the water."

Peng Daesan said this and convinced himself.

\textit{That's right. If I let that one loose in the Dragon-Phoenix Assembly defenseless, who knows what kind of trouble she'll cause.}

It's an unavoidable decision for the peace of the orthodox Wulin.

And so, Qing, with her excellent execution ability anyway, immediately rushed towards the Wulin Alliance.

Because Gong Sun-Yeye was there.

It was a simple principle, like why a mountaineer climbs a mountain.

However, since it was around the end of the Horse Hour and beginning of the Sheep Hour, about 3 PM, proper Zhongyuan people usually weren't staying in their lodgings at this time.

So they heard that she had gone to Changliang Tower for the Dragon-Phoenix Assembly meeting.

Changliang Tower was in the exact opposite direction from the Wulin Alliance, based on the inn where Qing was staying.

It was like working twice.

And so when they arrived at Changliang Tower in Kaifeng, it was a field full of men.

It wasn't the picture Qing had imagined of six or seven people gathered chatting.

It was like a general alumni meeting with seniors, juniors, and current students all gathered, using an entire floor for a noisy drinking party.

With almost all the rising stars of the orthodox faction gathered before a big event, the crowd was naturally large.

"Oh my. It's the Azure Dragon Association meeting. It seems the Phoenix Association is holding their meeting at a different location."

The Dragon-Phoenix Assembly meant the meeting of the Azure Dragon and Phoenix, with the Azure Dragon representing men and the Phoenix representing women.

"We came for nothing. I haven't revealed my face yet, so let's withdraw from here."

Peng Daesan changed his mind at the sight and slipped away quietly.

As Zhuge Lixian went in to ask about the location of the Phoenix Association meeting, Qing and Tang Lan-Ah were left standing there, receiving all the hot gazes of men who had discovered beauties.

More precisely, Tang Lan-Ah received them.

Because Qing was wearing a face veil.

That's when it happened.

Qing, spotting a familiar face, shouted:

"Ah, Sword Friend!"

"No, this voice, Sword Friend! Is it Sword Brother!"

Nan-gong Shencai stood up abruptly and welcomed Qing.

He spoke as if he recognized her by her voice, but really, there was only one person in the world who called Nan-gong Shencai 'Sword Friend'.

"But Sword Friend, what's with the face veil? Did you perhaps get a scar on your face? Don't be too disheartened if that's the case. A scar on the face means you stared down your enemy to the end, so for a swordsman, it could be said to be an honorable medal."

"Hmm! Sword Friend! If you say such things to a woman who really has scars on her face, you might get stabbed with that sword you love so much! But, as a swordsman, in the end, you should become a scabbard to embrace the sword blade. Not a dao scabbard or spear scabbard."

"Indeed! It wouldn't be right for any weapon other than a sword to take this life. I believe you, you must be Sword Friend for sure. This clear and precious statement woven together is a golden rule and great writing that only Sword Brother could make."

"Right. Have you been well?"

"What could have happened to me? How about Sword Friend?"

"Recently, my chest was split in half, from here to here, and from here to here, making a ten-character cross sword wound."

"Ooh! How splendid! It's a thousand-year regret that I can't ask to see it."

It was a half-and-half mix of responses that were hard to tell whether they were common sense or not.

It's splendid, but given the area, he won't ask to see it.

"As expected, I knew you'd understand. Unfortunately, Lan-Ah here treated it well so no scar remains."

"Ah. So it's Miss Tang."

"Blooming Poison Flower!" "Blooming Poison Flower!" "Blooming Poison Flower!"

The men who had been focusing on the only woman present shouted her title simultaneously as if they had made an agreement.

It was a sharp chorus as if they had rehearsed with their mouths in advance.

Qing just frowned behind her face veil.

\textit{What on earth?}

\textit{Is that admiration even strictly set to one, two, three, now, as if it's a time when it must be done?}

Nan-gong Shencai continued his greeting.

"We greeted at the last 70th birthday celebration, um, actually, we didn't greet because the young lady was only sticking to the Jade Qilin's side. What was it you said, that a wife can't mix words with other men when her husband is present?"

"Uwaah! You've got the wrong person! I never said such things! There are things you can and can't say to an unmarried maiden!"

Tang Lan-Ah denied it with a bright red face.

\textit{Hmm. I should ask Zhuge to make a collection of Tang Lan-Ah's quotes from the Grand Patriarch's, that is, Poison Grandfather's 70th birthday celebration.}

\textit{Interesting things keep coming out no matter how much you peel.}

And then Qing and Nan-gong Shencai loosened their swords and bumped their scabbards together.

Originally, swordsmen consider swords clashing to be a hundred times more insulting than shoulders bumping, so this was a greeting method showing true friendship tied by swords.

"So, Sword Friend, what brings you here?"

"Ah. Do you know where the Phoenix Association meeting is?"

"Ah. I see. The place was too small so we had to separate. The Phoenix Association should be in full swing at Liangyun Tower."

"Liangyun Tower. Hmm. Why didn't that Zhuge bastard just say one word."

Then in Qing's field of vision, she saw Zhuge Lixian excitedly chattering away without stopping his mouth.

Well, that's to be expected.

Qing immediately understood.

Anyway, she wasn't going to take Zhuge to the women's meeting, so she might as well let him talk properly this time.

Qing and Tang Lan-Ah struck out again and headed towards Liangyun Tower this time.

If they had sent a servant to find out in advance, they could have gone in one trip, but now they were moving for the third time.

"Qing'er, the Phoenix Association is war. It's different from the good-natured Azure Dragon Association where they all drink together as friends. You don't know about women's society, but it's a terribly cruel place where those bitches check each other, mock, and secretly bully."

It was essentially Tang Lan-Ah, who had just made her Wulin's debut, saying this to Qing, the Grand Elder of the Divine Maiden Sect, a women's sect.

But having seen how things work in the Bliss Palace, Qing did have a feeling of 'maybe, possibly'.

Although she didn't believe it at all since it was Tang Lan-Ah saying it.

"So Qing'er, just trust me. I'm the number one ranked Blooming Poison Flower Tang Lan-Ah among the Five Flowers of Wulin. Just stick close to my side."

"Hmm. If you say so."

Of course, since Qing was tall, it looked to everyone like Tang Lan-Ah was clinging to her.

In fact, Tang Lan-Ah was clinging to her.

And so Qing entered the tower.

In Tang Lan-Ah's words, it was the fox den of the Phoenix Association, a cruel battlefield where they crush each other's dignity without swords and spears.
