\chapter{Coming Soon (8)}

Meanwhile, Chen Sui was on high alert.

After all, wasn't it Tang Lan-Ah, with whom she didn't have a good relationship even in polite terms?

Even without Tang Lan-Ah, the five members of the Five Flowers of Wulin couldn't be called close at all, they were on terms of badmouthing and criticizing each other without restraint.

Summarizing their criticisms roughly, it went like this:

The Poison Flower uses poison. Moreover, she doesn't distinguish time and place, and after getting caught at the 70th birthday celebration and lying flat on the ground crying and playing the victim, everyone got sick of her.

The Sword Flower thinks anyone with a bigger chest than hers is either a Wulin criminal or her parents' enemy. But she has the smallest chest in the world.

The Wise Flower looks down on others, pretending to be smart. If you talk to her for just a moment, you realize she'll live her whole life without friends.

The Snow Flower has no expression or emotion. They say it's a side effect of ice arts, but she's completely inhuman with no humanity. She doesn't say more than two words, so all her lines are either yes or no.

You might ask why all these flowers called the Five Flowers of Wulin have flaws, but originally, if you set out to find faults, anyone can become a flawed human.

Therefore, the greater the affection for the other person, the more understandable the flaws and the more prominent the strengths appear.

It's just that the Five Flowers of Wulin don't get along, so only their flaws stand out.

Anyway, it was natural for Chen Sui to be tense with the Poison Flower next to her.

First of all, she didn't know why she had come to sit next to her.

Wary that she might use poison, she first threw out a weak check.

"By the way, Lan-Ah. You seemed really close to that face-veiled Miss Ximen earlier. What kind of person is she that the great Poison Flower follows her around?"

Translation: Why is someone at the level of the Five Flowers of Wulin acting like a servant, tending to a veiled ugly woman?

"You. If you go around with your chest out like that, doesn't it get congested? But was it originally that heavy? Did you put something underneath to support it?"

Tang Lan-Ah responded by cleanly ignoring and countering.

"Wh-what are you saying. It's always been like this? I didn't put anything in?"

"I'm just saying it out of concern. Isn't the human body healthiest in its natural state, and gets sick when it's not? If cold gets into your chest and you forcibly lift and fix it, you'll have big trouble later with blood clots. If you're not careful, it might have to be cut off."

Chen Sui was uncertain.

She thought it was an attack, but it wasn't?

What is this? Why is she pretending to be concerned?

"Hmm. You applied powder instead of oil? Is it because many blue veins are showing through? That's a really bad sign. If you get a breast tumor, you really have to cut it out."

"Oh, that's not good, is it really serious?"

Chen Sui was intrigued.

Tang Lan-Ah was also well-known as one of the few female physicians.

"I can't tell well with my eyes because of the powder? I think I need to palpate to know. Should I take a look now? Tomorrow everyone at the Dragon-Phoenix Assembly will see. We should look when it's just us women."

"Oh, okay. Sure…"

"It's not just ‘okay, sure'. You should say ‘please, Dr. Tang', right? Or are you going to go to the medical hall and have your chest examined by some old man?"

It was a problem caused by the lack of female physicians.

Women often endured even when they were sick, because they were embarrassed to be examined.

"Do you know what happens if it's really a breast tumor? They'll call all the medical students and say, ‘Look at this, this is a breast tumor. If you touch it like this, you can feel the lump, this is blood cancer that's spread from liver cancer. Each of you touch it and remember this sensation.' They'll call all the disciples in the neighborhood and knead it like rice cakes?"

Chen Sui's face turned pale.

"I, I'll ask you, Lan-Ah. Can you take a look? Actually, it's been feeling a bit stiff lately…"

"Hmm. I'd like it if you were a bit more polite."

Chen Sui bit her lip.

Then Tang Lan-Ah smiled as if she was being generous and said.

"Well, a doctor can't choose patients. Let's set up a screen. Everyone heard, right? If anyone's curious, line up. While we're at it, if you have any pain you can't talk about, I'll take a look."

Chen Sui realized her mistake.

\textit{This bitch is now trying to win people over with medical skills instead of checking with poison.}

\textit{If she openly provides medical care to me, who's known to be on bad terms with her, anyone from the Phoenix Association who has any pain will run to her without hesitation.}

\textit{Tang Lan-Ah, this terrifying woman.}

\textit{And that Ximen Qing woman too.}

\textit{To act like a servant to this extent, just how much power does that veiled woman have to make her do such unsuitable things?}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Did you have fun?"

"Yeah. I saw the Iron Pagoda with Miss Gong and ate lots of snacks. The Iron Pagoda is impressive even seeing it twice. Oh my, I'm so full. Snacks are surprisingly filling."

"…? Was that your business?"

In Zhongyuan, 'snacks' refers to all light refreshments excluding side dishes.

Silkworm pupae skewers are snacks, steamed buns filled with red bean paste are snacks, tanghulu, sugar candy, and even ginseng preserved in honey are all snacks.

So if you ask for all types available in the store, even eating just one bite of each is enough for a full meal for an adult.

"Ah, right. I heard there's another Dragon-Phoenix Assembly tomorrow, what should we do? Are you going too, San? They said there will be lots of delicious dishes."

"I went for a walk earlier, and it was so comfortable with my face covered. Tomorrow I should go eat the famous Guantang Xiaolongbao and Guojie of Kaifeng."

"Oh? What's that, if there's something like that you should have told me first. Damn, I'm so full."

"I didn't say we're going to eat now. And I just heard about it during my walk today."

"Guantang Xiaolongbao, I can tell what it is just from the name. It's dumplings filled with hot soup since it's Xiaolongbao with tang. What's Guojie?"

"They say it's made by pouring pancake batter when frying jiaozi to make it crispy."

"Ah. Sounds delicious. If only I wasn't so full."

"You can eat it tomorrow, can't you?"

"Tomorrow I have to go to the Dragon-Phoenix Assembly. They said there will be lots of delicious things."

Peng Daesan's eyebrows twitched.

However, Qing couldn't read it because of the bamboo hat.

"Banquet food might be fancy but there's not much substance. It's either cold from being prepared early in the morning and left out, or the taste is compromised from reheating."

"What? If the food at a banquet is terrible, why go to a banquet at all?"

"Usually, the purpose of a banquet isn't the food."

"Hmm. Is that so? Still, since we're here, we should at least greet people. I promised to see Sword Friend and Daoist Changbin too. Xiang'er was there too. Do you know Zhuge Xiang?"

"Do I need to know?"

"Well. It's good to know people all around, right? Anyway, then you'll be separate tomorrow too? How will our San handle being lonely. Ah. Get some Xiaolongbao and jiaozi for me too."

Twitch twitch. Peng Daesan's eyebrows moved again.

"Are you planning to eat cold dumplings? Hmm. By the way, are you planning to keep wearing that at the Dragon-Phoenix Assembly?"

"Hmm? Is it rude?"

"No. If you don't want to deal with annoying situations, it's better to keep wearing it."

"Well, that's true. When I stayed at the Tang Clan, those five or six brothers were so burdensome. The way those men threw hot gazes, ugh, it gives me chills. I really hate it. What, are they crazy?"

Qing expressed her disgust.

\textit{How should I put it, like gazes dripping with honey?}

\textit{The way those pepper men always tried to make eye contact with sultry gazes, it was truly a disgusting, terrible experience.}

As they were passing time with such meaningless chatter, Tang Lan-Ah returned to the inn and sat down next to Qing, leaning against her.

"Ah. I'm so tired. Examining patients after so long really drains my energy. Why does everyone have something wrong with them? If you're sick, you should go to a doctor…"

"What, you were examining patients? At the Phoenix Association? Wow, you did a good thing? But why?"

"Just had something to check. I thought maybe, and it turned out I was right. Ah, are we sleeping together today?"

"What, who decided that?"

Then Tang Lan-Ah looked at Peng Daesan and imitated a Chihuahua.

With that kind of arrrr feeling.

"Then are you going to keep sharing a room with him? Even if he's a harm-less-friend, men and women should be separate, sharing a room isn't right. You say something too? Who should Qing'er sleep with?"

"Someone might think we deliberately got just one room."

"That's right. Since we didn't deliberately get just one, there's no problem if Qing'er comes with me, right?"

Peng Daesan frowned.

\textit{If you ask like that, doesn't it make me look like I deliberately got one room?}

\textit{I can't say no, so the answer is already decided, but if I say go ahead, a strong feeling of rebellion and stubbornness rises.}

\textit{This is all deliberately provoking, she was really a nasty woman.}

But if he insist on sharing a room, he'd really become a guy making advances, so in the end, all he could do was nod his bamboo hat with a resentful heart.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Dragon-Phoenix Assembly gathering wasn't a temporary event, but just whenever there was a big event in the orthodox Wulin, the rising stars gathered in one place and that was the Dragon-Phoenix Assembly.

When men gathered it was the Azure Dragon Association, when women gathered it was the Phoenix Association, and when they were together it was grandly named the Dragon-Phoenix Assembly.

Of course, it was an important gathering befitting its grand name, as it was a place for the next generation who would lead the future orthodox Wulin to build friendships.

"Do you want to try wearing a zhanxiong too, Qing'er? I think it would suit you really well."

Zhanxiong's ‘胸(xiong)' means chest, and ‘襢(zhan)' is an uncommon character meaning to take off the upper garment.

The style Chen Sui was wearing at yesterday's Phoenix Association was called zhanxiong, or 'explosive breast outfit.'

For reference, 'explosive breasts' in Chinese means exposing the chest, and has nothing to do with size.

Qing answered incredulously.

"Hey. I'm from a Daoist sect too, you know?"

"Ah. Right. Qing'er was a Daoist too."

That's right. Ximen Qing was a Daoist cultivator!

It was an unexpected identity.

And Daoists wear Daoist robes.

Whether it's allowed during personal time might differ slightly between sects, but at least in official settings, you have to wear Daoist robes.

"Then can you wear it later? Does the Divine Maiden Sect not allow it?"

"Not particularly…"

"Then, let's go get one made after we finish today. I'll do it for you. Okay?"

"Hmm. It looked suffocating just to look at."

"No it's not? It's totally comfortable? Actually, many women wear it because it's comfortable. When you lift and fix it like this, it doesn't even shake and it's comfortable."

"What? Lan-Ah, you wear it like that too?"

"It's hot in summer. It's so cool."

"Really? Do all Sichuan people dress like that? This summer it's Sichuan. You have a room at the Tang Clan, right?"

Tang Lan-Ah burst out laughing.

"Qing'er, you seem to be misunderstanding, it's not some daring outfit or anything? You just lift the long skirt to your chest, expose your collarbone, and wear a breezy outer garment, that's zhanxiong."

"But yesterday, that, Lily? How can someone's title be Lily? Talking Lily?"

"That Lily is a bit, too low. Usually, no, nobody goes that low? I don't know how she walks around like that. If you're going to do that, just go naked. That's a sickness too, a sickness. You know what she does? When men look, she pretends not to notice and brings her arms together to lift them even more."

"Hmm. She was an admirable lady. But then, was she the only one dressing like that? No wonder I thought it was my first time seeing it. Sichuan is canceled. Doesn't seem like there's anything to see."

Then Tang Lan-Ah said with a giggle:

"You. Why are you looking at others when you have the best? I palpated them all, and there's only one perfect in shape, size, texture, and weight. It's not that I'm weird, but once you experience this, you really can't help it. Let me just. Wow, yes. This is it. This, wow, this is, wow. Really, wow. I can't express it."

"Now you're boldly touching. Won't you stop?"

At this, Tang Lan-Ah withdrew her hand with a gentle smile.

In fact, Tang Lan-Ah had completely changed her strategy.

Medical books say that when people are repeatedly exposed to stimuli, they eventually become accustomed and stop feeling anything special.

Based on this, it was a strategy called 'making it natural.'

If someone walks around doing a handstand in the marketplace, at first people might think they're possessed or doing some strange training.

But novelty only lasts a day or two, after a month everyone gets used to it.

They think, ah, that person is just someone who walks around doing handstands.

It becomes natural like this.

This was exactly what Tang Lan-Ah was aiming for.

And it was gradually showing effects.

Tang Lan-Ah was just silly, but basically a terrifying villainess with a loose screw.

"Come on, Qing'er, let's go now. I'm feeling great energy from the morning, my strength is surging."

Tang Lan-Ah said with a refreshing smile, naturally wrapping her hand around Qing's.

Ximen Qing, full-scale sortie to the Dragon-Phoenix Assembly.
