\chapter{Coming Soon (2)}

The three great ancient capitals of China are Xi'an (Chang'an), Luoyang, and Kaifeng (Liang).

They share the commonality of developing based on the productivity of the vast plains stretching from Hebei-Henan-Hubei-Hunan in an era when primitive farming methods were all there was.

Among them, when it comes to Kaifeng, you can't leave out the massive canal.

With the canal entering the city center, you could board a ship in front of government offices and reach Beijing to the north, pass through Luoyang to Xi'an in the east, or go southwest through Hangzhou to the sea, making it the center of China's water transportation.

This connects to all three major river systems of Zhongyuan - the Yellow River, Yangtze River, and even the parasitic Huai River - creating a grand waterway.

"Hmm. Wake up now. Go up and sleep."

"Huh? Don't wanna…"

Qing answered drowsily without opening her eyes.

"If you don't want to, what, are you going to sleep uncomfortably here? We've got a room, why not sleep comfortably in a bed?"

"I want to sleep here…"

"Hmm. Then, I guess you'll have to stay in the carriage. I'm going."

Peng Daesan unknowingly pulled a 'You live here, mom's going home' move.

Come to think of it, it's quite a universal human sentiment.

"Go well… see you later…"

However, Qing was also the worst of the worst.

Peng Daesan reached out his hand, then withdrew it and rubbed his chin with a troubled expression.

No matter how much of a friend she was who didn't know the distinction between men and women, it wasn't right for him to act that way either.

Instead, Peng Daesan put his head close to Qing's ear and whispered in his characteristic low frequency.

"Wake up when you come to your senses."

"Eek! Wow, what. Chills."

The effect was tremendous.

It was so tremendous that Qing opened her eyes wide and immediately sat up, and Peng Daesan barely avoided a collision between the head of a man with precious beauty and a skull as hard as ten-thousand-year cold iron but actually empty inside.

"Wow, chills, really what. Don't do that. That."

Qing rubbed her arms vigorously and grimaced.

Of course this happens when you're lying comfortably drunk on leftover sleep, and suddenly a man's overly sensual voice digs into your ear.

"Hooh."

Peng Daesan's eyes flashed.

It was the flash of someone who had finally discovered a weakness in an annoying friend.

But that was only for a moment, as there was something covering and pressing down that sharp starlight gaze, a large bamboo hat with a face veil hanging from the end covering the Jade Qilin's gracious face completely.

It was something Peng Daesan had hurriedly given money to a servant to buy in the morning, so the performance of the face veil wasn't particularly excellent.

Just a cheap face veil with a pleased arc faintly visible through the transparent lower face.

"What, you decided to cover your face now? Didn't you say you wouldn't cover it because you had nothing to hide?"

"Thinking about it all night, I realized I'm the only one suffering harm anyway. The dirty one should avoid others. I thought it wasn't right to step in filth and be disgusted while insisting on going straight. I had a servant get one."

"Right. You thought well. That's exactly right. Then I'll do the same."

Qing put on her face veil.

Seeing this, Peng Daesan asked.

"Was it originally that color?"

"Yeah. Chaolei washed it well. Wow, fragrant. She doesn't seem like it, but she's truly a heavenly woman. So attentive too."

"Unlike someone."

"Well, that's because I'm a man. And actually, I could be a heavenly woman too, you know? I just choose not to."

"That's exactly what it means to be already ruined."

As he said this and got out of the carriage, Qing stretched out.

"Oh my, I'm dead tired after traveling all night. Really, people should sleep at night, not do other things."

At this, Peng Daesan shot back, dumbfounded.

"What were you doing with your eyes closed in the carriage? You've got quite a thick face to not wake up even once."

"Hey, sleeping in a carriage doesn't count, you know? It doesn't feel like I slept at all. Haah, huaaah."

Qing yawned with her mouth splitting wide open.

Because a woman with a large mouth is one of the representative conditions of an ugly woman in Zhongyuan, it's taboo for women to even make a sound when yawning, so they turn their bodies and cover their mouths.

Of course, Qing doesn't know, and even if she did, she'd say what does it matter since she's not ugly anyway.

Peng Daesan clicked his tongue at this manly openness.

"Go finish sleeping and we'll meet for lunch. The room is on the fourth floor, second from the end, marked ‘Red Pine'."

Peng Daesan, still sitting in the carriage, said this while holding onto the door that Qing had flung wide open.

"What, San. Where are you going?"

"Every inn is full of guests, so I barely got a room even paying extra. I'll catch some sleep in the carriage and come find you around lunchtime, so don't cause any trouble and stay put."

With the Wulin Conference right around the corner, all guests had made long-term reservations.

If he hadn't covered his face, he would have stayed at the Wulin Alliance Heavenly Martial Team's lodgings, but now that he was hiding his identity and running away, he didn't want to do that.

So he was saying he'd sleep in the carriage parked at the stable.

"Hey, why sleep uncomfortably in the carriage, oh. I was short-sighted. With San's personality, there's no way you could have slept. You must have stayed up all night with your eyes open worrying something might happen."

"…I did doze off."

"A tired person should sleep in a bed. I've slept a lot anyway, San should sleep in the bed. Don't talk about men and women being different and all that, I'll just sleep on the floor."

"Don't do that."

Peng Daesan said this and then, as if he had been waiting for it, lightly jumped out of the carriage.

Qing's face veil tilted subtly.

"Hmm?"

"Why are you doing that? Ah. By the way."

And Peng Daesan's semi-transparent lips stretched out long.

"There are two beds, but you say you'll sleep on the floor. Did living as a beggar for so long make the floor comfortable?"

"Ah, the beds are separate? What, then why did you say you'd sleep in the carriage?"

"Well, should I have said let's sleep together since there's only one room but separate beds?"

"Ah. That's right. You'd become a weird guy."

Qing understood and thought.

\textit{So he could only get one room, but he couldn't bring himself to say let's share a room, so he was waiting for me to bring it up.}

\textit{What's with this troublesome guy?}

\textit{But the carriage owner is San, the person who got the room is San, and the money spent on it is San's.}

\textit{So what can I do?}

\textit{Who am I to complain when I'm just tagging along?}

\textit{No, that's not right.}

\textit{I was just going to play with Chaolei and Jun in Changyuan and come slowly, but I came along because I felt sorry for friendless San.}

\textit{So I had the right to demand anything proudly on this Kaifeng trip.}

If San heard this, he'd retort asking if she had begged timidly when going to Luoyang or Mount Hua.

Peng Daesan slept soundly until it was almost the Horse Hour.

It was natural since he had stayed up all night guarding the carriage without a wink of sleep.

And then he was a bit surprised, because Qing was sleeping again on the opposite bed.

\textit{She slept, woke up, slept in the carriage, woke up, came up to the inn and slept again?}

\textit{If left alone, could she sleep all twelve shichen of the day?}

He had only just caught up to Qing's martial arts realm this year despite her being so lazy, to the point where he felt self-deprecating.

After that, he woke her up to feed her lunch, and immediately piled snacks in front of her, which she then gobbled up noisily and asked:

"So, what are we doing now? What's famous here? Are there any sights to see?"

"Could you ask one thing at a time? First, we should go to the Alliance to greet the Alliance Leader, hmm. We don't have to if we hide our faces. I like it. Maybe I should have covered my face from the start."

"See? It's comfortable when you cover it."

"It does damage my dignity a bit though."

Face-covering bamboo hats like this are commonly seen in Zhongyuan.

Usually worn by boatmen/ coachmen, they're functional attire that blocks the sun when it's out, rain when it's falling, and the face veil protects against water spray/ dust.

However, since the perception of boatmen and coachmen is very poor, it's a lowly item for a high-class young master to wear.

"What are you saying? It's not like anyone will recognize you anyway, why would your dignity be damaged?"

"Hmm? Is that so? You have a point."

"So, what are we doing now? I'm bored to death after just lying around."

"There are two famous Buddhist pagodas in Kaifeng. One is tall and one is short. There's also the largest market in Zhongyuan. And, though you probably won't be interested, there are also temples enshrining King Wu, Yue Fei, Zhang Liang, and Bao Zheng respectively."

If Zhuge Lixian were here, he would have poured out all the stories related to these, but Peng Daesan tended to provide just the minimum information.

Two pagodas. One tall, one short.

Temples, you probably won't be interested anyway.

And the largest market in Zhongyuan.

"Hmm? Bao Zheng? I feel like I've heard that name somewhere."

At this, Peng Daesan's eyes trembled.

"I mentioned four names and you only know one? And why Bao Zheng of all people?"

"Actually, I don't know. Bao Zheng? Is he a dancer? Anyway, temples don't sound like there's much to see. And Buddhist pagodas are in temples, right? How tall and big could they be?"

The Buddhist pagoda Qing was thinking of was like National Treasure No. 1, the one engraved on the 10 won coin.

\textit{How tall could a pagoda be, maybe twice a person's height-}

\textit{…is what I used to think.}

"Wow. It's so tall."

After eating a hearty late lunch and facing the brick pagoda soaring high into the sky at a temple called Kaibao Temple, Qing couldn't hold back her admiration.

Of course, you'd be amazed after seeing an eighteen-zhang high, thirteen-story pagoda built with bricks.

The Iron Pagoda is named the Iron Pagoda.

It's not made of iron, but called the Iron Pagoda because the bricks are dark like the color of iron.

"We've seen the tall one, so we don't need to see the short one, right? Shall we go to the market? Markets mean street food."

"You're going to eat again after eating all that?"

"Actually, there's not much room left. So let's walk. We need to digest as much as possible and then carefully select what to eat. You should have told me before lunch. You tricked me well."

"Really. You have a talent for leaving people speechless."

"Isn't anything a talent if you hone it?"

Since she never loses an argument anyway, responding would just lead to an endless series of nonsensical words.

So Peng Daesan closed his mouth at this point.

But just because Peng Daesan closes his mouth doesn't mean Qing follows suit and closes hers.

Before she left for Jianghu, she wasn't particularly talkative, rather closer to being a good listener than a talker.

But when a person lives in a foreign land, especially with China's friend culture being what it is.

There are levels even among friends, and you climb up strictly created steps from acquaintances.

They even notify and inform you when you move up a level.

‘From today, I've decided to consider you a close friend.'

This common saying in China, doesn't it mean they didn't consider you a close friend before?

When a person gets hung up on food, they tend to overeat, and if you live steeped in loneliness just trying to survive, you can't stand moments of silence and fear emptiness of sound.

"Oh. What's that? Rice wrapped in leaves?"

"It's honey rice. Rice mixed with honey."

"Why mix honey with rice? Sounds unappetizing."

"Honey is expensive, so they usually put in boiled fruit."

"Ugh."

"Don't you like sweet things?"

"Sweet things and rice are separate, you know? They shouldn't be combined. Sweet things should be sweet, rice should be salty and spicy and sweet, hm? Can it be sweet? What sweet dishes are there? Braised ribs? Ah, I want braised ribs."

"You really say whatever comes to your open mouth."

"Ha. Isn't friendship supposed to bloom in conversation? Fine. I'll shut my mouth tight. Don't be surprised if it suddenly gets quiet."

And Qing really did close her mouth.

Since Peng Daesan wasn't the type to initiate conversation, the two just strolled through the market.

Suddenly, Peng Daesan realized he felt very unfamiliar.

Just by putting on a face-covering bamboo hat, isn't it so comfortable without women fanatically following?

It felt stupid to have hesitated, thinking that hiding his identity and sneaking around was like running away under their pressure.

"Ah, San. What's that? It looks a bit gross."

"It's chicken heads."

"What, chicken heads again? What kind of place is this where they eat even the heads of chickens? Regardless of men, women, old or young."

"…? Then do they throw them away?"

Chicken heads, along with duck necks, are representative snacks in China.

But chicken heads were a bit too much, so in the end, after much deliberation, Qing chose well-roasted duck necks.

Qing's voice was muffled again as she gnawed on the duck necks.

They say you can tell if someone is Chinese or a barbarian just by watching them eat duck necks.

When eating duck necks, you strip the meat, break the bones, roll them in your mouth, clean them completely without leaving even a tiny bit of meat, then suck out the marrow and spit it out on the ground.

Qing, in her fifth year in Zhongyuan, could be said to have become fully Chinese.

As Qing was nibbling on duck necks and curiously looking at all sorts of things from Zhongyuan that had flowed in via water transport, it happened.

Suddenly, Qing's left hand shot out to the left and grabbed a man's wrist.

As the sensation of bones grinding traveled up her palm, ah, yes, this is it.

It's been quite a while since I've seen blood.

"Aagh!"

Only the man's miserable scream echoed.
