\chapter{Coming Soon (4)}

"Hey, isn't that Zhuge and Lan-Ah? What brings you here- Ah. Everyone ends up gathering anyway."

"Have you been well, Sister?"

"Qing'er!"

"Why so much- No, come here!"

As Tang Lan-Ah ran over with an extremely delighted expression, Qing snorted but then changed her mind and opened her arms wide.

Tang Lan-Ah attempted a body tackle.

The effect was minimal.

This was because force is determined by speed and mass (excluding the cosmic mystery of True Qi), and Qing's body wasn't weak enough to be unable to withstand even a light girl's charge.

As Qing took a stance to receive her, planting her foot, Tang Lan-Ah flew into her arms, wrapping her arms around her neck.

At that moment, a warm, nutty scent like heated milk wafted over.

"Are you hurt anywhere? If you have a fever or anything, don't hide it and tell me, okay? It'll be troublesome if wounds get infected, so let's check later when we go up. By the way, I heard you were in prison. Those guys there didn't treat you badly, did they?"

"They did treat me badly…"

Of course, Qing was the perpetrator, the one who acted badly, but.

When the imprisoned women tried to bully her, she injected some manners into them.

She thought about confiscating their food because she was hungry from the meager rations that didn't even touch her liver, but no matter what, taking away food was too much, so she let them eat.

"How did it go? The old man Ban's son?"

"It's his grandson, Sister."

"Whether it's a grandson or son, it's all the same for a nineteen-year-old. Anyway, isn't he a grown child?"

"That's true. The grown child has returned to his elderly grandfather, so you don't need to worry. Miss Jian said she'd take him and settle at the Xue Family Trading Company, do you know the place?"

"Well, it would be hard to keep operating in Zhumadian. That's good. It's a small shop run by a friend. Ah. I'm hungry. Have you all eaten? Hey, waiter!"

After moving to a private room, Qing took out her frustration from the day and a half wasted in vain on the innocent food.

"Sister, are you actually tasting anything?"

"Yeah. It's delicious. Ah. Right. Zhuge, do you know about the Shadowless Divine Hands?"

"The Shadowless Divine Hands! You mean the exclusive martial art of the Shadowless Divine Thief! Yes, I learned about that interesting thief when I was eleven years and seven months and eight days old, while learning military tactics from Master Zhang Xue…"

"You really talk too much… Somehow it seems like you've gotten even more talkative. Doesn't Lan-Ah listen to your stories?"

"Well, Miss Tang doesn't listen to anyone's words, not just mine. Ah. She does listen well to Sister Ximen's words. It's strange."

"Wh-who listens well to whose words."

"What? Are you not going to listen to me? Lan-Ah, I'm really disappointed."

"No, I'll listen. I will listen, but…"

"Where was I? Ah, the Divine Thief…"

To summarize Zhuge Lixian's long explanation:

The Shadowless Divine Thief refers to a lineage of thieves passed down through generations as a mysterious figure of single-person transmission.

They usually target wealthy merchants, government offices, and occasionally rich unorthodox sects, distributing the stolen money to the common people.

They don't specifically target bad rich people, but generally, rich people are bastards with a very high probability.

Robbing bastards and distributing money is a good deed, and even if they rob one good rich person out of a hundred, it's not a big problem since the money will be distributed to the public anyway.

Thanks to this, they're sometimes called righteous thieves.

But basically, they were ambiguous thieves between righteousness and selfishness.

"Hmm. Somehow the evaluation seems harsh."

"A thief's offspring is still a thief's offspring. My writing teacher, Master Zhang Xue, said they're petty thieves who take their cut and then show off by distributing the leftovers, a mongrel among dogs."

"So what about the Shadowless Divine Hands? Damn, when did you smoothly change to talking about thieves?"

The Shadowless Divine Hands or Shadowless Divine Grab is a grappling technique.

Grappling uses the characters for 'capture' and 'seize'.

In other words, it's not a technique for hitting and striking, but a skill for subduing by pushing, pulling, binding joints, or disturbing balance.

While general martial arts like fist techniques, hand techniques, palm techniques, claw techniques, etc. take a strong offensive approach with striking, hitting, and kicking, grappling chooses the subtlety of softness overcoming hardness.

However, in the case of the Shadowless Divine Hands, it's specialized in a different direction.

It's said that its stealthy hand movements, which leave not even a shadow, can remove even a woman's undergarments without her noticing, making it the best pickpocketing technique under heaven.

"Huh? Isn't that comparison a bit much? And, that's a bit… It would feel quite empty and uncomfortable if your underwear was gone."

"This comes from a historical anecdote about a bet between our senior, the Celestial Martial Emperor, and the Divine Thief. The bet was whether the Divine Thief could steal without the woman noticing, and it's said the Divine Thief won."

Afterwards, when the Divine Thief apologized and returned the underwear, he got slapped hard.

Then the Celestial Martial Emperor apologized on his behalf, saying he had ordered it, and disappeared with the woman.

Originally, the Celestial Martial Emperor was also famous for being handsome.

They say the Divine Thief had to return feeling defeated despite winning the bet.

"Hmm. He deserved that slap. Well, I guess so."

"Isn't that guy a total pervert? What kind of person does that? Did he put some kind of numbing powder on his hands? It's creepy. Uh, hmm…"

Qing's superhuman hearing caught Tang Lan-Ah's muttering to herself like a breath inside her mouth.

-Numbing powder…

And then, placing a plate of boiled and fried pork ribs in front of Qing, she said:

"Qing'er, tonight it's just us friends, you know."

"Hey. What numbing powder? Don't you remember when my chest was split open, I didn't even use numbing powder and had it stitched up raw? That's really creepy."

"Ah. I-I don't know what you're talking about. And what, what! Yeah, what! It's just between women. It's not like it'll wear out!"

"Now you're being quite bold, aren't you?"

Qing's eyes narrowed.

At this, Tang Lan-Ah boldly met her gaze and put strength into her eyes.

Of course, her pupils were trembling and her complexion was pale, showing she was frozen stiff, but that courage alone could be acknowledged-

\textit{No, what courage is this?}

Then something occurred to her.

"Hmm? Come to think of it, how did you manage with lodgings? I heard every inn was fully booked."

"There are guest houses provided by the Alliance. That's right, Sister. Would you like to visit the clan's guest house? How Xiang'er is making such a fuss about wanting to see you. You must have become quite close in such a short time."

"Kids usually like me. The Murong kid also made a big fuss calling me Sister."

"Perhaps it's because you match and understand them well. After all, your mental age matches perfectly- Ow!"

Ding! With the sound of a small bell ringing, Zhuge Lixian grabbed his head.

"Don't feel safe just because you're far away. My head flicks don't care about distance. Somehow it seems like you're getting more and more cheeky? You just call me Sister with your mouth."

"Where in the world is there someone who uses the Buddha's Palm for head flicks…"

At this sight, Peng Daesan's eyebrows twitched.

Originally, Zhuge Lixian was friendly and polite, respectful to everyone, calling them brother or sister even if they were just a year apart.

However, such politeness also comes with a certain distance, so even though he's friendly with all the rising stars of the Dragon-Phoenix Assembly, he doesn't have anyone he's particularly close to.

He does stick close to Hwangbo Uncheok, but that's because they're cousins.

Moreover-

"Wait. Buddha's Palm?"

"Didn't Brother Peng know? Sister is the successor of the Buddha's Palm."

"This is the first time I'm hearing about this."

"Well, that's because I didn't tell you?"

At this, Peng Daesan's eyebrows twitched again-

"What? Why are you twitching your eyebrows? Is there a custom of telling friends all the martial arts you've learned? I don't know what San has learned either?"

"That's. Hmm. I see…"

"Wait! What was that just now! San? Are you two in that kind of relationship? No! This is invalid, I can't accept it, I won't. I can't allow it!"

At that moment, Tang Lan-Ah interjected again.

Peng Daesan flinched, looked at Tang Lan-Ah, and made his characteristic expression of disgust when seeing women.

\textit{Come to think of it, this woman was here.}

The Poison Flower of the Tang Clan.

An arrogant woman who thinks she's the best and looks down on people.

On the other hand, she's also a selfish woman who thinks the whole world revolves around her, and should revolve around her.

He had seen her twice when there was an event in Sichuan.

A terrible woman who made him sick of her in just two meetings.

He had forgotten about her because she hadn't been acknowledging him yesterday and today, and he hadn't been paying attention to that side recently since he hadn't been bothered by women.

Peng Daesan's expression rapidly turned cold.

But that was only for a moment.

"Even if it's Young Master Peng, this isn't right. Seducing our innocent Qing, this must be that, right? Approaching under the guise of a pure friend. Right! That's what I was going to say! No, how could you get just one room! How could you!!"

Tang Lan-Ah's voice grew louder towards the end.

It seems she got more and more heated even as she spoke.

"Even if our kind-hearted Qing'er says it's fine because there are two beds, shouldn't the young master go sleep in the Heavenly Martial Team's quarters!? Isn't this a ploy to stay in one room and then link them together when rumors spread later!!? Hey, isn't this completely a bad guy move!!"

Peng Daesan pointed at his own face with an incredulous expression.

A gesture asking if she was really talking to him.

"What, how annoying. Just because you have a good face, are you showing off now or what? Do you think I'd act like a silly girl, giving you my liver and gall bladder over that mere face?"

"Ha. This is ridiculous."

"I'm the one who finds this ridiculous?"

Tang Lan-Ah shot back without backing down.

Peng Daesan's voice dropped an octave.

"Don't you remember what you said to me at the Grand Patriarch's 70th birthday celebration?"

"Ugh."

"Didn't you suddenly come up and say you'd allow one wife and one concubine? And what else did you say? That you hoped I'd have a child after five years because your body would be ruined?"

"Uuugh."

"Well, you didn't act like you'd give me your liver and gall bladder even then. You just acted like the main wife without anyone's permission."

It was truly the behavior of a villainess.

If this wasn't a martial arts story but something else, she'd be the villainess who appears at the beginning and throws a glass of wine at the protagonist.

In return for moisturizing once with skin-beneficial wine, the basic price is the annihilation of her entire family including herself, and in severe cases, even her soul might be caught and suffer eternal torment in the flames of hell.

Therefore, Tang Lan-Ah should be grateful for her entire life that she was born in Zhongyuan.

"Th-that time! I was young too!"

"Hmm. Then, does that mean you have no feelings for me now?"

"Ha! Do you think all the women in the world like you? You're really annoying."

Peng Daesan's expression twisted.

At this point, Qing felt it was time to intervene.

"Our Lan-Ah spoke well! That's right! Correct!"

"See. It's only me, right?"

"Yeah, yeah. But what was that? You said you'd allow one wife and one concubine? Did you really say that? You said to have a child after five years for body management?"

"It was also our first meeting."

Peng Daesan tattled.

Tang Lan-Ah's face turned bright red as if about to explode.

Then Qing snorted.

"You weren't much better at our first meeting either? What did you say? ‘This is a technique I've never seen before'? And ‘Your chest is so vulgarly large, minus a hundred points'?"

"…It wasn't a hundred points."

San subtly averted his gaze.

With one about to explode and the other unable to raise his head, the argument naturally came to an end.

"As expected of Sister! After enjoying as much as you wanted and hearing as much as you wanted, you seized both sides' weaknesses and subdued them at once! This slow-witted brother is moved by your vile tactics! Truly excellent! It's truly marvelous and mysterious!"

"Right. Zhuge. I'll let it slide this time, so you can put away the flattery. And if you want to defend, find a material other than glass. The glass shards will get stuck in your hair, you know."

"Yes, Sister. I'll keep that in mind."

And so, after the meal ended.

Naturally, while sipping tea that had been ordered, Qing said:

"Ah. By the way, that young lady. Gong… Gong Chan? Hmm? Who's Gong Chan that it's sticking to my mouth?"

"Ah, you mean Gong Chan? Gong Chan refers to-"

"Don't be noisy. It's Gong Sunyeye. She's said to be from the direct line of the Gong Clan."

Peng Daesan cut off Zhuge Lixian's chatter.

It could be said to be a very appropriate measure.

Qing asked again.

"Right. Anyway. She proudly revealed her identity, so it must be a famous clan, right? Then you must know where they are? Where is that young lady now?"
