\chapter{Coming Soon (7)}

Gong Sun-Yaoyi\footnote{公孫堯藝. Gong Sonyeye 공손요예 in the original text} was new to Jianghu.

Her life as the decisive weapon for her clan's destiny of restoring their surname is nothing but training day after day.

She starts the day with training, eats breakfast and trains.

She even eats lunch at the training ground and trains until dusk, then after dinner with family, it's more training.

Then she sleeps in a separate building next to the training ground, ending the day.

So how excited must she have been approaching the Wulin Conference?

Friendship where she could seriously discuss martial arts with peers her age, clash swords, share breaths, and run together towards the end of martial studies!

As a result, the Phoenix Association women's evaluation of Gong Sun-Yaoyi was like this:

'A girl who's cocky because she knows some martial arts.'

'Talking about not being a woman but a martial artist, then what is she if not a woman, is she looking down on people or what?'

'Seems like her eyes roll back whenever she sees a man, wanting to rub bodies under the pretext of sparring.'

'Does this country bumpkin want to rub shoulders with famous Wulin sects?'

Of course, Gong Sun-Yaoyi's behavior was very bad.

It's good to have pride as a martial artist before being a woman, but originally pride was something you should feel alone.

You shouldn't say things like 'Why are you talking about trivial things like adornments, clothes, ideal types for romance and marriage?' in front of everyone at the Dragon-Phoenix Assembly, including the men of the Azure Dragon Association.

Moreover, the men responded to those words by standing up, applauding, and cheering 'Right, right, a true martial artist!' (Sword Lunatic was largely responsible for being the first to stand up and shout, stirring things up)

Whether they were usually serious about martial arts training or not, she had thrown a huge insult at all the women who had dressed up prettily in front of the men.

If Qing had seen this scene, she would have said it was like declaring at the first drinking party with all university seniors and juniors gathered, 'Women who came all the way to university, are you not studying to become great people, but spending money on makeup and clothes to cling to men and aim for marriage?'

Of course, Gong Sun-Yaoyi might feel wronged too.

She was just doing as she was taught, it was what the strict clan elders always said.

'Get up, don't whine like common women. Know that it's shameful.'

'What's the big deal about periods? Do you think enemies will go easy on you for three days a month? You lacking girl.'

'Adornment is a pathetic trick used by women who can't become martial artists, realizing their lack of ability and trying to seduce men to change their fate. Don't even think about touching such filthy things.'

People naturally, without interaction with others, come to think everyone in the world lives like them.

How could she help expecting that the promising new stars of the orthodox Wulin would naturally be proud martial artists regardless of being men or women?

This is how the Dragon-Phoenix Assembly gathering became a terribly awful place for Gong Sun-Yaoyi.

But when she tried to skip it saying she would train instead, she was scolded harshly for treating lightly the socializing for the clan's long-cherished wish, so she couldn't skip it either.

Even when she tried to mingle with the men, the martial artists, it was all in vain.

The Azure Dragon Association members either wanted to chat among themselves having men-only conversations or dreamed of romance trying to impress the women.

So naturally, Gong Sun-Yaoyi became like a non-existent person.

Even when she appeared, no one acknowledged her (except for types like Cao Haocai), no one talked to her when she sat down, and no one stopped her when she got up from her seat.

It was days of silently sitting in her seat, trying to maintain a composed expression while spending lonely time with no one talking to her, then returning to her lodgings.

It was especially terrible on days when the Azure Dragon and Phoenix Associations held separate meetings, and that was now.

It was in this situation.

"Miss Gong? Could we talk for a moment?"

Gong Sun-Yaoyi flinched.

It was the face-veiled woman she had seen in the market a few days ago.

It was during Gong Sun-Yaoyi's first deviation, when she had slipped out to wander the market alone, unable to bear the ignoring anymore.

She was the woman who had caught the pickpocket, but Gong Sun-Yaoyi had run away, afraid that either the truancy or the hair ornament would be discovered by her clan.

"What, what is it? I have nothing to say."

"Come on, don't be like that. Let's go out for some fresh air, everyone, I'm borrowing Miss Gong for a bit, okay?"

Then one of the women sitting at the same table answered flatly.

"That woman isn't part of our group. Do as you please."

"Ah. I see. But why so cold? Did you two fight? Come on, it's better to get along. So, I'll do as I please?"

And then she reached out her white, almost pale beautiful hand towards her wrist.

She, whose life had been training, surely wasn't careless enough to easily offer her wrist to a woman who had been flirting with men- Snap.

Gong Sun-Yaoyi's wrist was caught, and she had a blank expression.

Then she was pulled with force, but what strength, no, my goodness.

Gong Sun-Yaoyi was dragged along helplessly.

"Wait a moment, miss, I have nothing to say-"

"I do. And didn't they say to do as I please with Miss Gong? So it's my will."

"I never gave permission!"

"Come on, are you a prince? Do I need permission just to talk? And I've never asked permission from a prince either?"

And so when they came out of the tower, she said let's walk a bit and dragged her along the canal path in front of the tower.

"Wow, there are so many boats. Don't you think?"

"Now will you say what you wanted to say? And let go of my hand."

"If I let go, you'll run away again, right? I'm an expert in escape, and I can see you're already calculating the angle."

"Who said anything about running away?"

"Forget it. Weren't you alone sightseeing in the market then too? You seem to like sightseeing? Then, have you seen the Iron Pagoda? Let's see, around there, ah. Can you see that?"

Following the woman's finger with her gaze, the dark top of a pagoda peeking out between buildings came into view.

For it to be visible despite being quite far away, its original height must be enormous.

Gong Sun-Yaoyi unknowingly let out an exclamation of admiration.

"Wow…"

"Looks like you haven't seen it yet. When you see it up close, you'll exclaim ‘wow' three times - it's so high, so big, so wide. Go see it sometime later. It's worth seeing."

"More importantly, what did you want to talk about?"

"Ah. Right. A few days ago, you know. A rude pickpocket reached for a pretty woman's bag, so I unknowingly executed justice?"

"I told you it wasn't me-"

"But because the pretty woman who could prove my justice ran away without a care, I became a foul-tempered sword-wielder and got locked up in prison. For two whole days on that cold prison floor, with only two tasteless meals a day. And the punishment was flogging. Do you know flogging? It's a punishment where they tie you up and beat you with bamboo rods."

Gong Sun-Yaoyi's heart sank.

\textit{Was it that serious?}

"Who asked for your help? And if I had known it was that serious, I wouldn't have… I didn't know."

"It's fine. They said they'd let me off if I paid sixty wen, so I paid sixty wen and didn't get beaten."

"Sixty wen…"

"Anyway, here. This ornament is yours, right? I was going to keep it as payment for the beating, but I'm being generous. I'll return it."

"I told you it's not mine."

"Then let's say it's not Miss Gong's. Wow, I found a very, very pretty hair ornament on the street, and it looks perfect for our Miss Gong. Here. A gift."

Gong Sun-Yaoyi received the hair ornament in a daze.

And then the woman said:

"It's nothing else, I just wanted to apologize and that's why I brought you out. I thought the hair ornament looked pretty so it must be precious and wanted to return it. I didn't know Miss Gong would be so embarrassed. I'll keep my mouth shut from now on, so don't worry."

"Ah…"

"And you don't need to worry particularly because I just dealt with the pickpocket because I saw him. You know how you pick up trash when you see it? I just can't help but act when I see human trash. So even if it wasn't Miss Gong, I was destined to pay sixty wen someday, so you don't need to worry about it."

Gong Sun-Yaoyi looked down at the hair ornament.

It was a gift her mother had given her secretly when she was young, saying it was their little secret, when she was crying quietly during harsh training (because she would be scolded more if she cried).

"Well. My business is done. Miss Gong can go back to your business now. Hmm. I wonder when everyone will come back from playing."

The woman said this and turned her back without lingering, walking away briskly.

Gong Sun-Yaoyi looked at the hair ornament in her hand, then towards the Phoenix Association hall in Liangyun Tower, then turned her head to look at the tip of the Iron Pagoda peeking out in the distance.

And then looking for the retreating figure of the woman-

"Wait! Miss!"

She hurriedly ran out and caught up with the woman.

"Oh? What is it? No returns."

"Um, I'm sorry, but if it's not too much trouble, could you guide me to the Iron Pagoda? I'd like to see it up close…"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Iron Pagoda is just a tall, large brick pagoda.

It's surprising and awe-inspiring when you first see it, but it's not still surprising when you see it a second time!

To think such technology existed in primitive, ancient, uncivilized China!

"Wow…"

"Originally it was a wooden pagoda twice as tall, but it was struck by lightning and burned down, so they rebuilt it with non-flammable bricks, halving its height."

Qing boasted, pretending to know the story she had just picked up.

"My goodness, it's so tall even now. It's a shame I couldn't see its previous form."

"Right? But you know, Chinese people exaggerate, so no one knows if it was really twice as tall. Honestly, I don't believe it."

"Is… that so?"

"Well, if it's like that, I could say the same. There was a hundred-story tower at the Divine Maiden Sect that reached the sky where we met fairies, but oh no, it caught fire while playing with fire with the fairies and disappeared. What, you don't believe me? How can you be so sure about something from the past? If you can't bring evidence that it didn't exist, then it existed."

At Qing's words, Gong Sun-Yaoyi's eyes widened.

"Was there really such a tower?"

"Do you think there was? If there was, it would be called the Divine Tower Sect or Heavenly Tower Sect instead of the Divine Maiden Sect."

Qing answered with a snicker.

She's so naive for someone new to Jianghu.

"Ah. Right. I'm not sure if I can ask this, but can I?"

"What is it?"

"I heard that Miss Gong's given is Sun-Yaoyi, but I was told it's much better to call you Miss Gongsun, so I've been calling you that. Is that not rude or anything?"

"Ah. That. Actually, our clan's original surname was Gongsun. Because we're a clan descended from the primordial ancestor."

"Ah. Xuanyuan."

Qing knows at least the genealogy of the Three Sovereigns and Five Emperors of Daoism.

It was thanks to diligently copying it last winter and having it ingrained in her head.

The first emperor of China, with the surname Gongsun and given name Xuanyuan. He's commonly called Xuanyuan-shi, but here ‘shi' isn't a surname but an honorific title attached to mythical beings.

"…So we're trying to restore our surname."

Gong Sun-Yaoyi revealed her clan's circumstances.

"Ah. Why did they arbitrarily cut someone else's surname in half? That's really mean."

"You shouldn't say such things carelessly."

"Why, isn't it normal to curse when no one's around? Don't your family members curse the emperor? I bet they do."

"…Just a little."

"See? Hmm. Are you hungry? I'm not hungry but my mouth is curious. Does Miss Gong like snacks? No, there can't be people in the world who dislike snacks. What kind of snacks do you like?"

"Uh, I don't really…"

"What, you don't like snacks? I just said that, how can you say you don't like them to my face?"

"It's not that, I haven't really tried many so I don't know the names. That fried… square, sweet with red bean filling…"

Then Qing answered with a laugh as if it was ridiculous:

"One out of four Chinese snacks is fried, square, sweet, and filled with red bean paste. This won't do. Today is the day we empty out a teahouse of snacks. Let's go. I'll feed you snacks until your stomach bursts."

The money Qing had earned through her nuclear bombing of punishment was no ordinary amount.

Moreover, when there's a man in the group, Qing doesn't have to spend money.

When there's a man in the group, if a woman takes out money, it becomes a rude action that disrespects the man.

Surprisingly, the men didn't have much complaint about this, because men who did complain would be kicked out of manhood with words like 'Tsk tsk, a man who doesn't even have money to spend on women, are you a beggar?'

Of course, it had to be taken into account that women had no way of getting money except for pocket money.

Basically, since women had no income, it was a structure where the money-earning men took full responsibility.

After that, Qing indulged to her heart's content.

She boldly ordered every type of snack available at a well-located teahouse.

"Miss, you can't eat like that."

"…? But I'm going to eat it."

And then Gong Sun-Yaoyi was shocked at the ensuing snack massacre.

No matter how much she said she wasn't a woman but a martial artist, wasn't this beyond the difference between human and beast, let alone woman and martial artist?

Wouldn't even a pig starved for three days not eat like this?

Anyway, Gong Sun-Yaoyi did taste a little of each type, so for the first time in her twenty-seven years of life, she realized what her snack preferences were.

And then Qing, who hated silence with no voices, said whatever came to mind, and Gong Sun-Yaoyi, who wasn't very talkative, awkwardly responded.

After passing time like this for a while, as it started to get dark, Qing said she should probably head back now.

As Qing was saying goodbye, Gong Sun-Yaoyi hesitated and asked:

"Will Miss Ximen be attending the Dragon-Phoenix Assembly tomorrow?"

"I'm not sure. I might go? I might not go?"

"Why is that?"

"It might be because of a friend who doesn't like to show his face. I might go if I have nothing else to do. Ah. I should see Sword Friend and Changbin too, so I guess I should go. Hmm, high probability of attending?"

"I see."

Gong Sun-Yaoyi nodded and seemed like she wanted to say something, hesitating, but in the end just said goodbye and farewell.

Qing just tilted her head.

\textit{What, so anticlimactic}, she thought.
