\chapter{Dragon-Phoenix Assembly (14)}

In fact, it wasn't really anything new.

It was the same in Luoyang, and always like this on the way to Mount Hua, so women glaring daggers when next to Peng Daesan was almost a daily occurrence.

At those times, Qing would just smile and busy herself looking at the women's faces, so she hadn't really paid attention to it until now.

But strangely, it was upsetting her mood.

\textit{Why are they making a fuss about me hanging out with my friend? These nobodies are getting on my nerves.}

Originally, if someone hates you for no reason, you should give them a real reason to hate you.

Qing briskly approached and stuck her hip right next to Peng Daesan.

"Haiyaa, why are there so many women? Don't they have anything better to do? San, I'm thirsty. Get me some sweet fruit tea. With ice floating in it."

"Are you alright?"

"Hurry. I said I'm thirsty?"

"Our Qing'er says she's thirsty. Why are you dawdling with your butt stuck to the chair? Aren't you going to bring it quickly?"

Peng Daesan frowned.

As they say, the nagging sister-in-law is more hateful, so Tang Lan-Ah chiming in beside her was more annoying than Qing boldly demanding tea.

No, wasn't she the woman who used to follow him around talking about being the main wife?

Why has she suddenly turned into an evil minister of the enemy country, sticking close and provoking?

"You really have no manners."

"What? Between us. Can't you bring a cup of tea when I'm thirsty? Are you embarrassed to be ordered around with so many onlookers?"

Then again, faint exclamations spread as background noise here and there.

Peng Daesan's expression went blank for a moment, then a smile slowly spread across his lips.

Since it was a ploy to provoke the onlookers, there was no reason for Peng Daesan not to play along.

He'd done it once before, and it was fun.

"I see. Between us."

When Peng Daesan brought fruit tea with ice floating in it, Qing glanced at it and said:

"There's too little ice. Don't you know if it's like this, it'll all melt and just be bland and not even refreshing? No, do I have to explain even simple things like this? Ha, you're just a pretty face with no brains. What are you doing? Aren't you going to bring it again?"

There was a clamor of gasping.

At that sound, Peng Daesan caught on to Qing's intention.

Peng Daesan answered with drooping eyebrows and a pitiful expression:

"I'm sorry. I'll bring it right away."

One way or another, they were in sync.

Peng Daesan also had a lot of pent-up feelings towards the onlookers.

When it came to teasing those women, his mind worked exceptionally well.

"What's this, you poured fruit tea over ice, this is just a lump of ice, what fruit tea? Are you protesting because I told you to put in a lot of ice? What, are you upset because I told you to bring it again?"

"You misunderstand. I just thought you wanted it cold-"

"Forget it! Don't you know cold things are bad for women? This is really ridiculous. Just the right amount of ice? Not too much, not too little. You don't understand this? Can't you do even this simple thing? Not too much, not too little, appropriately, the right amount. Why can't you do this simple thing? Ha, you're so stupid."

"I-I'm sorry. Please wait a moment."

Peng Daesan hurriedly brought another cup of tea.

"Hmm. It's a bit much, but this much is… It's not quite to my liking, but I guess you tried. But now that I look at it, I don't really crave something cold. Bring me warm tea instead of cold."

"Alright. I'll bring it right away."

And then Qing was being difficult again.

"Aish, it's too hot? Are you trying to burn the roof of my mouth? There's not a single thing I like. Are you really doing this? Making me upset. Forget it. I'm leaving? I'm going to leave."

"I-I'm really sorry. I was thoughtless. How should I serve it for you?"

"Then, blow on it. To cool it down."

At this, Qing held the cup right up to Peng Daesan's lips.

Peng Daesan blew on it and sat down, looking completely under her thumb, doing everything she asked despite all the scolding.

The watching women's insides were bursting.

Many women were crying, shocked at having their pure hearts trampled.

Women who couldn't bear to watch anymore started leaving for the upper and lower floors.

"How is it? Is the temperature right?"

"Let's see. Hmm. It's fine. Well, for San. Why didn't you do this from the start? Use your head, your head. Really. You might have a pretty face, but inside you're really, ha, so stupid."

"I'm sorry. Um, will you stay and not leave?"

"I don't know. Ah, right. I saw a hair ornament at the market that was pretty? They said it came from the Western Regions and asked for two guan of gold. It's shaped like a flower like this. Look, wouldn't it be perfect if I stuck it right here in my hair?"

Qing pointed at her hair that couldn't even be seen because of the face veil.

"Two guan of gold for a hair ornament. What kind of hair ornament is so-"

"Don't you think it would suit me?"

"Hmm."

"Don't you think it would suit me?"

A chill ran down Peng Daesan's spine.

\textit{Hmm. What is this pressure?}

Even knowing it's obvious acting, he was starting to get scared.

"…Alright. I'll buy it for you-"

At this, Qing abruptly stood up.

"I'm leaving. I'm really dumbfounded."

"Why, why are you doing this?"

"San, don't you know why I'm doing this?"

"If it's about the hair ornament, I'll-"

"Forget it. San is always like this. Don't you know why I'm doing this?"

"That… I'm sorry."

"Sorry? What are you sorry for? Tell me."

"Well…"

Sweat slowly beaded on Peng Daesan's forehead.

\textit{Is this… really acting?}

"Ha. Really. When did I ask you to buy it? I just said it was pretty. But what? Acting like you have no choice. What? There's a limit to making someone look bad."

"That, that wasn't my intention."

"Then? If that wasn't your intention, what was it? I heard that if Jian Buxi's gaze just lingers on something while walking, it flies over neatly packaged a few days later. I'm not even asking for that much, am I? How can a person be so thoughtless? I'm not a beggar. Do you think I'm doing this because I don't have that bit of money, just two guan of gold?"

"I'm sorry, I, I was short-sighted."

"Haah. I really can't live like this. Forget it. Let's stop talking about this now. I don't need the hair ornament, so don't waste a lot of money buying it."

"Uh… Al-alright."

"But you know, that ornament. It has tiny red jade and purple jade inlaid like this, what's that pattern called? Mandala? My goodness, even San would say ‘wow, it's pretty' just looking at it with his eyes? You know I don't usually say things are pretty when I see them. Right?"

"Hmm. Can we stop now? I'm starting to get scared."

Finally, unable to endure anymore, Peng Daesan raised the white flag.

He couldn't bear the great fear he had never felt even in front of the Daoist Gentleman's sword force.

Qing clicked her tongue regretfully.

"What a shame. I still had a bit more."

"You're truly terrifying. So, what was the right answer? Should I buy it or not?"

"Half and half? It could be really asking to buy it, or just saying it's pretty? If it's the former and you don't buy it, it's over, and if it's the latter and you buy it, it could be over because it's burdensome to the tune of two guan of gold."

"Hmm."

"If I had to pick one right answer, it's just to break up. If a woman comes at you like this? The inner thoughts are that I'm doing you a favor by meeting you? How can you communicate with a woman who thinks like that? Just break up, or if you really have your heart stolen and feel you can't live without this woman, well, I guess you'd have to live getting beaten."

"Hmm. I see."

Peng Daesan shook his head with a disgusted look.

Qing patted his shoulder, giggling.

"San doesn't need to worry? San has absolute superiority in this area, so women wouldn't dare act like this. If San just lowers his voice and grits his teeth saying ‘Is that so?' once, they'd grab your pant leg and beg for forgiveness while crying, you know."

Then Qing alternately sipped cold and hot tea, and suddenly spoke as if she just remembered something:

"Ah. San is surprisingly sensitive, so you probably won't get nagged like this. Thanks for being considerate earlier. I just had a moment of intense reflection yesterday, you could say."

Seeing as he even called her name which he doesn't usually do, he must have been quite worried about the shameful behavior she showed yesterday.

At this, Peng Daesan subtly averted his eyes.

"So, I'm going to stop coming to the Dragon-Phoenix Assembly now and just train at the Wucheon Pavilion. Sword Friend agreed to look at my sword, and if San wants to spar together, come over anytime, ah, tell Chaolei to come too."

"You mean Nan-gong hyung?"

"Honestly, Sword Friend's realm is a bit low, but it's not easy to win in sparring. Maybe it's because I'm lacking in basics. There are lots of rooms at the Wucheon Pavilion, so come over without hesitation."

"Hmm."

"It seems the Zhuge family isn't coming today. I should tell Xiang'er to come over too. I can send a message later. Hmm. Have I seen everyone I needed to? Sword Friend, Changbin…"

That's when it happened.

A young voice cut off Qing's words and a tiny thing came running.

"Ah, th-that, no, Sister Qing! It is Sister Qing, right?"

"Oh? Jun'er! What brings you here? Oh my. Wow, our Jun'er, how did you recognize me?"

"Well, your voice is exactly the same."

Given his hobby, Murong Jun was exceptionally good at distinguishing voices.

"Yes, that's very clever of you. Have you been good and not saying bad words all this time?"

"Um. Well. I did a few times… But you said it's okay to do it for family, so I did… Is that alright?"

"Hmm. Family can't be helped. But you didn't do it otherwise, right? Wow, how can you listen so well? Come here."

Qing sat Murong Jun on her lap.

Then Tang Lan-Ah's sharp voice pierced her ear.

"Who's this kid? How can he sit on a lap I couldn't even sit on, Qing'er, how could you do this to me? I know how to sit on laps too-"

"What nonsense are you talking about. Why are you coveting my lap when there's a perfectly good chair? Here, this strange and pretty, well, strange sister is Tang Lan-Ah. She's a bit weird, so good Jun'er should understand."

"Hello. I'm Murong Jun."

Murong Jun bowed politely.

Tang Lan-Ah's eyes were still unkind.

"If you're Murong Jun, aren't you Sword Flower's brother?"

"Ah, you know my sister? Are you perhaps my sister's friend?"

"This kid is saying terrible things. Hey. There are things you can and can't say to people, how can you ask if I'm friends with your sister? Your sister doesn't have friends, you know?"

Tang Lan-Ah said bluntly.

She could have spoken more kindly to a nine-year-old child, but Tang Lan-Ah is originally a woman who's rude regardless of age or gender.

"Oh, really…?"

"Ha. Has your sister ever brought anyone home saying they're her friend?"

"Well, I don't think so…"

"See. I told you your sister doesn't have friends."

"Ah, so sister doesn't have friends…"

"Right. So don't go around saying- Ow."

Tang Lan-Ah received a light tap on the head from Qing.

"This girl has no filter with kids. Don't listen to what the strange sister says because it's strange. And this handsome hyung here is Peng Daesan."

"Ah, so it's you! Nice to meet you! The brother-in-law I've only heard about! Um, I've heard a lot about you."

"Ooh, family reunion. Historic moment. All of Zhongyuan wept. True story of emotion."

Qing burst out laughing.

Peng Daesan's eyebrow twitched.

"Kid. What do you mean brother-in-law?"

"That's what sister said? Aren't you the Jade Qilin expert Peng Daesan? Or do you just have the same name?"

"I am that Jade Qilin. Your sister seems to have misunderstood. There's no such thing."

"Oh, um. Sister Qing said not to talk carelessly about family matters. Right?"

"Wow, Jun! How clever of you."

Qing ruffled Murong Jun's hair.

He was a pretty little kid who listened very well.

"I don't know what your sister said, but originally your sister will take in a son-in-law, so she can't marry me, the heir of the Peng clan. Your sister probably made a, um, joke."

Unlike Tang Lan-Ah who doesn't go easy on children, Peng Daesan had enough consideration to choose his words.

"A son-in-law? What's that?"

"Hmm. You know that when people marry, the woman usually lives in the man's house, right?"

"Yes."

"The opposite, when a man lives in the woman's house, is called taking in a son-in-law. But I'm the heir who has to continue the family line, so I can't live in my wife's house. Do you understand?"

"Ah! I understand. Thank you."

Murong Jun bowed his head.

Peng Daesan's expression was strange.

"He's completely different from his sister."

"How is he? Quite cute, right?"

"Quite. For a child, he's quite quick on the uptake, isn't he?"

Peng Daesan readily acknowledged.

Just not throwing tantrums and being able to communicate makes him one of the cutest among his peers.

\textit{But why is he alone again?}

\textit{He did usually go around alone, but...}

"Jun'er, how did you come alone?"

"Ah, I came with sister. Sister is with the Phoenix Association people, and I, ah! That's right!"

Then he spoke as if he just remembered:

"Sister Qing, do you know who bullied our sister? I've been looking for them to teach them a lesson, but if it's alright, could you help me find them?"
