\chapter{Dragon-Phoenix Assembly (16)}

Qing climbed the stairs with dignified steps.

The staff followed behind, and some onlookers who judged watching a fight would be more interesting than observing Peng Daesan's face joined in, checking the atmosphere.

So on the seventh floor, with the two facing each other, Murong Zhuji was the first to speak:

"You. If you think I'm going to thank you, you're greatly mistaken. Who caused all this in the first place? Giving medicine after causing the illness?"

At this, Tang Lan-Ah immediately flared up:

"Wow, that one's manners are really terrible. Qing'er, terrible, there's no need to consider someone like that, okay? No matter how much of an enemy, shouldn't you at least say thank you once after that? Hey, kid, what do you think? Is this how your sister should be acting now?"

"Um… Sister?"

"What, what! What did I do wrong! Wasn't it wrong to make people misunderstand when there's nothing between you two in the first place!? You set up the situation to cause misunderstandings and then blame the person who fell for it!?"

It was Murong Zhuji's bold rebuttal.

Murong Jun's eyebrows and shoulders drooped.

His large eyes, exactly like his sister's, were trembling moistly, causing ripples.

"Jun, Jun why are you like that? Why are you looking at me with those eyes? Don't do that. Aren't you going to take sister's side?"

"U-um…"

"Tsk tsk. Well done, really."

Tang Lan-Ah clicked her tongue.

Murong Zhuji frowned deeply.

\textit{How on earth did she become such a loyal maid? Is she really the same person who used to spew poison about daring to speak to the master without permission from the main wife?}

More than that, her brother wasn't much help.

Rather than not being helpful, he was becoming the driving force turning the triangle in her conscience.

\textit{I need, I need a spokesperson to take my side too.}

Murong Zhuji looked around at her group.

Her group had been halved because they remained downstairs to observe the Jade Qilin's gracious jade face.

The group members subtly averted their eyes, looking elsewhere.

It meant they thought this wasn't quite right.

"Ugh."

"Forget it. There's no point in trying to take credit when I didn't help to receive thanks. Anyway, Young Lady Murong? How much longer do you need to continue this petty, childish war of words to be satisfied? Should I properly start here by saying the reason you're so narrow-minded is because there's no room for inner thoughts?"

"You, you! How can you say such things!"

"Haah. So, if you're confident you can win with words, shall we do it properly?"

"Eek!"

Murong Zhuji, who had already experienced being properly hit by Qing's words, swallowed her resentment.

To say there's no room for inner thoughts.

Even her lightly thrown punches dug in and tore things up, so she couldn't help but hesitate at the suggestion to do it properly.

"So let's sort this out now. Why are you doing this? Are you going to be this tiresome every time we meet?"

"You ask because you don't know? You humiliated me, completely humiliated me! And now you're going to act like the victim?"

"If you're talking about the drinking contest, wasn't it just that Murong miss couldn't handle her alcohol and acted out? I even conceded the match because I thought Young Lady Murong might make a mistake."

"Who asked you to concede? Did you think anyone would shed tears of gratitude for such a pathetic concession? Wouldn't anyone get angry if someone did that?"

"What if I hadn't conceded? Do you know that my drinking capacity wasn't even half full then? Honestly, even if I hadn't let you win, wouldn't the result have been the same, or wouldn't you have been even more humiliated by your drunken behavior?"

"Then you should have just left it like that! You just took all the good parts of being the kind, excellent, proper, good woman! Isn't it better to be the woman who lost to alcohol and made a drunken scene, rather than being made into an ungrateful bitch who got angry despite being shown consideration!"

"So you do know."

The cold gazes of the onlookers pierced Murong Zhuji's heart.

Murong Zhuji breathed heavily.

Qing let out a deep sigh.

"Wasn't it Young Lady Murong who originally set up the drinking contest arena on the first floor, gathering all the Dragon-Phoenix Assembly people? If we had just quietly had a drink together here on the seventh floor, you wouldn't have had to confess your, um, physical characteristics, right?"

"Don't call it physical characteristics! And, and if that's the case, then you should have spoken first, you should have said your drinking capacity was that good!"

Murong Zhuji's group members lowered their heads.

'Zhuji, how much more ugly things are you going to say?'

'If she had said her drinking capacity was good, you would have just kept sipping water until you showed signs of being drunk.'

"Well, alright. I'm sorry, Young Lady Murong. It's because I'm quite strong with alcohol. And I'm sorry for losing to you in the drinking contest too. I did it because I was worried Young Lady Murong might make a mistake from being too drunk, so there was no bad intention."

"Again! Again! Are you the only good woman!? Am I the only bad one!"

"If I had been weak with alcohol, I would have been the one to make a spectacle. Young Lady Murong must have been confident you would win too. So, what exactly made you so angry? To prepare such a grand trap?"

"You were the one who insulted me so harshly first! It was so humiliating, I've never heard such harsh words in my life!"

"Well, didn't Young Lady Murong pick a fight with me first? Honestly, I could laugh off comments about my face being ugly or my figure being vulgar, but should I have just endured when you insulted the entire Divine Maiden Sect?"

"That, that… it was just, well, I meant it looked like a beggar when you wore it, not that the Divine Maiden Sect robes were like that…"

Murong Zhuji made a pathetic excuse.

Because that was indeed a slip of the tongue.

Originally, proper female Daoists, that is, female disciples of the Nine Sects One Union, are rare. Among them, women who come up to the seventh floor are even rarer.

They either pretend to be lofty and stay on the fifth floor with their male sect brothers, or they just gather separately among themselves.

So when the women of the clans meet female disciples of Daoist sects, honestly, they're more like women of the same age who are sick of mountain life rather than Daoists.

These women are always busy criticizing their sects, saying how terrible they are as soon as they open their mouths.

So she had unconsciously looked down on them.

"Then, was that all my misunderstanding too? Alright. Then I'm sorry for misunderstanding, and I'll apologize for losing my temper in an immature way and saying harsh words. I'm sorry."

"Eek! So, why! In that way!"

Murong Zhuji was starting to feel dizzy.

Or it could be called fear.

\textit{This bitch is determined to bury me.}

Before, Murong Zhuji said it was your fault for making me misunderstand the situation, and Qing apologized.

And now she apologized again saying she misunderstood, so rather than arguing that this isn't different from what she said before, it just makes Murong Zhuji into a one-sided bad woman.

"Then you must have had reasons for picking a fight with me out of nowhere? What was your reason for saying I'm an ugly bitch and have a vulgar body as soon as you saw my face for the first time?"

Murong Zhuji felt wronged.

She felt wronged for being the only bad woman, and she was already upset about having small breasts, but now she was being insulted by a big-breasted woman, so she felt even more wronged.

So at this point, her sense of being wronged exploded.

"You, you shook those breasts in front of me first, showing off! You shouldn't do that! You shouldn't do that with such big things, right!"

Pitiful tears streamed down Murong Zhuji's eyes.

At this, the hall fell into a solemn silence.

Murong Zhuji surprisingly had a talent for creating a solemn atmosphere every time she exploded!

Qing awkwardly opened her mouth.

"Hmm. Young Lady Murong. I thought this might be the case. Do you pick fights with every woman with big breasts?"

"Yes! I pick fights! Are you satisfied!? Now that you've made me into the worst woman under heaven, are you happy! Why are you the only exception! It's always been like this, so why are you making such a fuss!"

"Was I too sensitive? Are you saying other people just accept your rudeness, I mean, your bad manners?"

"What? Rudeness? You've said enough-"

"Wait! That miss over there. Yes. That's right."

Then the woman who was pointed out hesitantly opened her mouth. She looked like someone who had probably been cursed at quite a bit by Murong Zhuji.

"Well, it's just because she does it every time, so we just think, ah, that bitch, I mean Young Lady Murong is at it again…"

"Then, you didn't respond in any other way?"

"I thought I'd meet my match someday. And also, since she's from the Murong clan, only someone like Sister Chen Sui could talk back, for a small clan like mine, there's nothing good that comes from making a fuss."

And then she awkwardly looked around, fidgeting.

"Miss? Do you perhaps have more to say?"

"Well, to be honest, it's not really unpleasant, because Young Lady Murong is the Sword Flower, and she looks at me with her eyes rolled back in envy, it's kind of a good feeling."

"Who, who's envious! I'm not envious at all! Who would be envious of those lumps of flesh!"

"Zhuji, stop. Stop it. Zhuji, wipe your tears, okay? Your makeup is all smeared. Okay?"

Murong Zhuji's group members rushed over, ready to subdue her if necessary, and were busy dabbing at her eyes with handkerchiefs.

Whether she gained courage from this or not, the young lady's words did start flowing.

"And even if Young Lady Murong does that, it's a bit… you know, for me to respond."

"What do you mean?"

"Well, it's not just anything, it's that kind of thing. You know, it's okay to insult people who don't have it, but the opposite isn't okay. Because it's pitiful…"

"That's right."

"That's true."

There were women nodding and agreeing with this. They were all women who had been insulted every time for the same characteristic.

There was a similar logic in Qing's homeland.

The poor can insult the rich, but not the other way around. Because that's too much.

Black people can insult white people, but not the other way around. Because it's too much for the master to insult the slave on top of everything else. Just let them insult all they want while picking cotton.

"What! Hey! Pitiful!? How! Just because you have those lumps of flesh, how can you look down on people like that! This is why I hate you big-breasted bitches!"

"Um, Young Lady Murong, I'm sorry but we're not looking down on people with small breasts, we just think Young Lady Murong is pitiful."

"Hey! You!"

"Well, if you're going to put something in there, you should fix it well, because the height is different on the left and right, or it moves around… I saw you hurriedly pulling it up from your solar plexus last time… But we couldn't say anything."

Thinking she might as well go all out, the testifying young lady spilled her pent-up words.

Murong Zhuji's blood pressure skyrocketed vertically.

Of course, hearing that they've been letting her off out of pity until now, she couldn't help but be furious.

"You, you, ugly ones!"

But no one seemed particularly affected.

Of course, even if they're not one of the Five Great Clans, they're still ruling families of local or small but long-established estates or cities.

Even if they're not as beautiful as Murong Zhuji, one of the Five Flowers of Wulin, they're not lacking in beauty anywhere.

Their backgrounds are similar too, so even if they can't compare to the Five Great Clans, they're all princesses in their own neighborhoods.

Murong Zhuji was most shocked by this.

"Everyone, everyone looked at me with those eyes, no, you shouldn't, how can you! No, don't, don't look at me like I'm so pitiful!"

Murong Zhuji took a step back, then shook off her group members and turned her back, running away.

Seeing this, Qing thought, hmm, \textit{now that it's come to this, maybe I did something quite mean}.
