\chapter{Dragon-Phoenix Assembly (2)}

As soon as Qing reached the seventh floor, her first impression was indeed that it was splendid.

It could be called a collection of thousands of years of Chinese costume history, with cross-collared modest tops and skirts tied at the waist, the same tops with skirts lifted to the chest, ornate outer garments with sleeves hanging down an inch.

Or the Ming-style outer jacket, the loose-fitting shenyi reaching from top to bottom, and more.

Among them, Qing found Chen Sui's figure.

And as she caught sight of Chen Sui awkwardly rising from her seat-

\textit{Wow. As expected. You don't disappoint!}

\textit{I believed in you, Blooming White Lily!}

Chen Sui wore a vest over her top with the collar meeting and crossing below her solar plexus, exposing her décolletage like an actress at an awards ceremony in Qing's homeland.

This was the early form of zhanxiong clothing from the early Tang dynasty.

Yesterday she had forcibly lifted it to create a thick protrusion upwards, but today she blatantly revealed a natural shape without support.

At this moment, Qing understood Tang Lan-Ah.

Since it's all visible to the eyes, just grabbing that, hmm, the impulse really can't be controlled.

But since Qing was a person of common sense, she decided to just keep it to herself.

"She's showing it all off again…"

"Why, it just looks good. Isn't this the outfit that Zhongyuan women should rightly emulate?"

"Then, do you want to try wearing it too, Qing'er? I'll have one made for you…"

"No, why do you keep offering to do things? And how can a Daoist wear such a lewd outfit?"

"Hmph. You went around naked in the Divine Maiden Sect."

"What are you saying? You're slandering an innocent person. The only times I'm without clothes are when I'm bathing and sleeping?"

"Normal people wear clothes even when sleeping…"

"Well, that's because I'm not a normal person but a special person. It's the sleeping method that only the top 0.1\% of sleep masters, no, supreme masters, take."

Qing spouted whatever nonsense came to mind.

Tang Lan-Ah was already used to it, so she just giggled and slapped Qing's shoulder.

Then a woman quietly slipped in front of Qing.

\textit{But that sense of distance, what's this, why is it like this?}

It was like how fighters square up before a match, blocking with their body while pressed close together, like Qing had seen before coming to Jianghu.

It was almost like the distance in a packed subway train.

\textit{Isn't it a bit too close?}

The woman standing right up against her, Gong Sun-Yaoyi, grasped both of Qing's hands and said:

"Ah, Miss Ximen. Did you get back safely yesterday? And did you sleep well last night? Um, and did you eat breakfast properly? You didn't have any trouble on the way today, right? I was so grateful and sorry yesterday, ah, come to think of it, I didn't apologize yesterday, if you have time, I'd like to treat you this time if that's okay with you tonight…"

"Miss Gong. First, calm down a bit."

Qing tried to stop Gong Sun-Yaoyi, who was spewing words rapidly.

Gong Sun-Yaoyi flinched in surprise and stepped back half a step.

"I'm sorry. It's my first time making a friend so I don't know what to say, I prepared in advance but I got nervous and my words got a bit long-"

As her words were about to ramble on again, Qing squeezed her hands gently and said:

"Miss Gong. I'm glad to see you too."

"Ah… Me too. Very much so. So this is how it's done."

Gong Sun-Yaoyi said with a small, somehow wistful smile like a wildflower.

Then there was a hand separating their hands.

"What's this! What's with this atmosphere!?"

"Ah. This is Miss Gong. Miss Gong, this is my friend Lan-Ah, Tang Lan-Ah. The Sichuan Tang Clan, you know?"

At this, Gong Sun-Yaoyi opened her eyes wide and then spoke in a lowered voice imitating a man, and in a man's speech pattern:

"Pleased to meet you. I am Sun-Yaoyi of the Gong Clan. I have long heard of your clan's reputation, so it is truly an honor to meet you like this."

"Wh-what's this, suddenly so polite…"

Tang Lan-Ah whispered, hiding behind Qing's back.

"Isn't she a bit strange?"

"That won't do. Miss Gong is completely new to Jianghu, it's her first time out. Before this, she was almost in closed-door training, just training constantly."

"Even so…"

Then Gong Sun-Yaoyi hesitated for a moment before quietly bringing up another topic.

"But Miss Ximen. About that, the way of address, um, if we're friends, shouldn't it be a bit softer, more comfortable like Miss Tang there of course I'm not forcing it and you don't need to feel burdened it's just my small thought-"

"Alright, Yaoyi, um, is the pronunciation a bit difficult? Then is Yi okay?"

Officially there's a seven-year age difference so she added "miss," but Qing originally didn't particularly distinguish age unless it was an adult.

It seems she wants to be more comfortable with her first friend, and well, there's nothing wrong with granting that.

"Ah! Yes! Please, I would be grateful…"

"You don't need to be grateful. Then Yi should speak comfortably too."

"Okay. No, alright. It's, not comfortable, so would you allow me to speak formally to you?"

"Alright. I grant you permission to speak formally."

"Ah, yes. Thank you… Huh?"

Qing giggled mischievously.

"Just do whatever is comfortable for Yi. I don't really care anyway. You should feel comfortable with friends, if you're uncomfortable then is that really a friend?"

"Ah. That's right. Somehow Miss Ximen feels like, yes, like an older sister. Of course, I don't have an older sister so it's just a feeling. I wonder if that's why I can't speak casually?"

"Ah. Yes, that's right. There's definitely that feeling."

Tang Lan-Ah nodded behind them.

Qing smiled smugly.

Well, it's natural since she's lived longer.

Chen Sui was still gauging the situation.

Since she had made up, sort of, with Tang Lan-Ah, there was no reason to be hostile to Qing.

Of course, the grudge from the hellish abdominal pain at the 70th birthday celebration wouldn't be easily forgotten, but it wasn't bad to maintain a relationship with a female physician she could rely on in emergencies.

\textit{Moreover, what's this, she completely won over the Gong clan girl?}

\textit{Well, even though she was a woman no one paid attention to, her skill was surprisingly impressive.}

\textit{She's a very hardcore woman among the stiff martial artist faction who had sharply criticized everyone in front of them, saying 'Don't flirt with men, just train martial arts, you pathetic women.'}

\textit{But now she's become a docile maid, smiling gently, to the point where I want to ask how on earth she melted her down.}

Then suddenly it occurred to her, ah, she said she was a disciple of the Divine Maiden Sect.

Wouldn't a sect entirely of women engage in this kind of power struggle every day? (No, they don't)

She must be a supreme master, a giant in women's power struggles where life and politics are indistinguishable! (This isn't true either)

Chen Sui swallowed her pride at this point.

It's frustrating, but you have to bow before a master.

Besides, she might be able to observe and learn from those mysterious skills up close.

If she could build a friendship and become allies, that would be even better.

Qing, with her arms held on both sides, thought 'Wouldn't this leave no hands to eat with?'

But if she removed Gong Sun-Yaoyi from her right arm, she would probably be very disappointed, and it didn't feel natural to remove Tang Lan-Ah and eat with her left hand.

As she was pondering what to do for a moment, suddenly a snow-white valley spread out before her eyes.

"Ahem, Miss Ximen. You just showed your face briefly yesterday, didn't you? I was disappointed that I couldn't talk with you."

"Ah. Miss Chen."

"Ah, come to think of it, you're carrying two swords. Do you use dual swords? I've heard dual swords are originally a difficult skill."

"Ah. I can do it, but I don't use it. Personally, I'm a bit…"

"Miss Ximen? Um. I can't see your eyes, but where might you be looking? Your head seems to be tilted down a bit…"

"Ah. I'm sorry. It's not that I have any ulterior motives, it's just because you're so pretty."

Chen Sui's eyes widened.

And then she shyly pretended to touch her elbow, which made Qing's eyes widen too.

\textit{Wow, what's this. The valley suddenly disappeared.}

Qing almost lost herself, but she snapped back to her senses at Tang Lan-Ah's words from the left.

"Look at that, look at that. Didn't I say she pretends not to show it but gathers them? She's so desperate to show off, I tell you."

Usually, when people gossip, they're careful not to let the person in question hear, but Tang Lan-Ah has no history of observing such etiquette.

A vein popped out on Chen Sui's forehead.

After she had approached first to make friends, to be treated like this.

But that was only for a moment.

"That won't do. And what's wrong with that anyway? It's definitely worth showing off. It just looks good, what's the problem. I'm sorry, Lan-Ah here has some rough edges to her personality, but her nature isn't bad."

"Pardon?"

"Miss Jin knows too, right?"

"Ah. Of course. I know very well. She's so nasty."

"Hey! I even examined you!"

"That was appreciated, but if you're going to be grateful, couldn't you speak a bit more nicely? You're throwing away all the goodwill you built up. I thought you were doing it because you felt bad about what happened before."

"Sorry? What am I sorry for? And who do you think examined you out of goodwill? I was just checking if anything was okay or not, um, no. Actually, I did try to show some goodwill. Aren't you grateful?"

Tang Lan-Ah said something incomprehensible and then quickly changed her words.

It was quite rare for Tang Lan-Ah, who usually says whatever she wants even if it kills her.

"Ah. Let me introduce you to my friends. This is Miss Xu Linlin of the Henan Xu Clan…"

After that, it was like a normal banquet.

Although she would have liked to eat voraciously, it was a bit disappointing that she had to use Ximen Surin-style beauty eating because she was attending as a representative of the Divine Maiden Sect.

Contrary to Tang Lan-Ah's evaluation that Chen Sui was an ill-tempered woman with nothing to show for except her face, she was surprisingly gentle and decent.

After the normal give and take of conversation, fumbling to find common topics, it eventually turned to martial arts talk, as they were martial artists.

The Guangdong Jin Clan is the originator of the famous Taiji Quan.

The ancestor Jin created Taiji Quan and became widely renowned under heaven, so a passing Daoist Zhang saw this and admired its mysterious principles, asking to learn and keeping it in his heart.

Later, Daoist Zhang created sword techniques based on the principles of Taiji Quan, forging it into the peerless divine technique of Taiji Wisdom Sword.

For reference, Daoist Zhang settled on Mount Wudang and established a Daoist temple, which became the world-renowned Wudang Sect.

"So the original, authentic Taiji Quan is our Jin Clan's Taiji Quan. However, these days, for some reason, many people consider the Zhang Clan's Taiji Quan to be the original, which is upsetting."

Qing searched for Taiji Quan in her martial arts window and something else popped up.

\textit{Taiji Quan had a red border, ah, is this it?}

Qing found the fist technique Taiji Wuji Quan with a dazzling purple border and quickly closed the martial arts window.

Anyway, she had no interest in fist techniques.

Unlike hand techniques that could be used with swords, fist techniques were created assuming no weapons at all.

Didn't her master say:

'Don't even think about learning fist techniques.'

'Human fingers were made with four long ones and one short one to firmly grasp tools, so Nüwa considered this when molding humans.'

'So naturally, you should hold a weapon in your right hand and have the empty left hand assist with hand techniques, so unless you're going to chant about not killing like those Shaolin monks, what need is there to learn fist techniques?'

And so, it seemed peace had come to the seventh floor.

There are various factions, but basically it's a three-way division of the Phoenix Association with the Lily, Sword Flower, and Wise Flower as the largest forces.

However, with the Sword Flower and Wise Flower absent, the remaining Lily was bound to be the victor of the seventh floor.

And it seemed all that conflict disappeared as the Lily extended a hand to Qing, but.

"Ah, I must have come to the wrong floor. Oh my."

With a lively voice, a woman who had climbed the stairs said, "I'm sorry, I seem to have come to the wrong building," and turned back to go down the stairs.

\textit{What's with her?}

As Qing tilted her head, she heard the sound of teeth grinding next to her.

It was the sound of Chen Sui's teeth gnashing.

Qing became curious about why, but soon lost interest.

It was because of what the woman who had just gone down said as she came back up.

"Ah, this is the top floor of the Dragon-Phoenix Assembly after all. I thought I had come to a brothel, not the Dragon-Phoenix Assembly banquet hall, because someone was dressed like a courtesan trying to seduce men with her flesh fully exposed."

"That damn flat bitch…"

"No, who dared to bring a courtesan into this precious gathering place for the esteemed members of the Phoenix Association? Oh! My goodness! Now that I look closely, it's not a courtesan but the Lily! Hehe, sorry. I made a mistake just looking at the outfit. Because there's no way a chaste woman would expose her flesh like that, I ended up mistaking you. Heheh."

\textit{Ooh. Personal attack. That's harsh.}

Qing was impressed.