\chapter{Dragon-Phoenix Assembly (6)}

The person who came to pick her up in the morning was Peng Chaolei.

"Ah, Chaolei!"

"Yes, Qing'er. Have you been well? Nothing unusual happened?"

"Come on, what unusual things could happen? Seeing Chaolei like this is the unusual thing. Seeing Chaolei first thing in the morning really boosts my energy. I'm so happy I could ascend to heaven."

At this, Peng Chaolei opened her eyes wide.

"You, talking like a romantic young master. If Qing'er were a man, I might have felt a little flutter? You're going to see the Alliance Leader, right? Get in."

Qing rode in the carriage towards the Wulin Alliance headquarters.

"Are you going to the Dragon-Phoenix Assembly after this is over, Chaolei?"

"Oh my. A woman my age would be criticized for going to such a place. It would be tactless to butt in while the juniors are having fun. There are some tactless, meddlesome friends, but I dislike it even for their sake."

"I think everyone would welcome Chaolei if you came…"

"They'd all be busy cursing inside. Besides, there's a separate gathering for the old Dragon-Phoenix Assembly members, so I should mingle with people my own age."

On the way, Peng Chaolei gave a brief explanation.

The Wulin Alliance!

When the Wulin Alliance was first formed and declared their alliance in front of the heroes gathered in Kaifeng Prefecture, the ones who regretted it, hitting the ground, were the Unorthodox factions.

Of course, they were terrified that the Orthodox and Unorthodox factions, who were dying to eat each other, were now going to band together to beat them up.

However, if they banded together, we could just band together too, so there was no reason to regret it.

The reason the Unorthodox factions deeply regretted it was because of the name.

Wulin Alliance? Are they the only ones in Wulin?

They regretted not forming an alliance first and taking that cool name.

Wulin Alliance means the Alliance of Wulin. (Nod)

Only martial arts sects that leaned slightly ambiguously towards the sunny side among the Orthodox and Unorthodox factions could join, so it was a cool naming that contained the spirit of not recognizing you Unorthodox Black Path rabble as Wulin.

"The Alliance Leader is a person called Cao Xuanliang…"

To become the face of the Wulin Alliance, not just anyone else, shouldn't you at least have your name on the list of the Ten Great Masters under Heaven?

So when the time approached to elect a new Alliance Leader, there was a fierce battle of wits among the Orthodox elders of the Ten Great Masters under Heaven.

They were busy showing humility and recommending other figures, passing around the punishment of pushing it onto each other because no one wanted to do it.

Of course, by the time you reach the level of the Ten Great Masters under Heaven, you could say you've achieved everything with wealth and fame as a given.

So they want to pass on troublesome positions to their juniors and focus on training themselves unburdened, or raising disciples.

Being the Wulin Alliance Leader just creates unnecessary work, and you just have to put on airs and act cool, so why would the previous generation's masters want to do it?

However, there was an exception during the election of the current Wulin Alliance Leader, when Ximen Surin stepped forward saying she would take it on.

Moved by this, the elders all came forward saying they would take on the Alliance Leader position, and as a result of fierce competition, Cao Xuanliang became the Alliance Leader.

"Master did?"

"Yes. If Elder Cao hadn't stepped forward, the Godmother would have become the Alliance Leader."

While listening to this story, the carriage passed through the main gate of the Wulin Alliance.

Peng Chaolei left saying she had to greet with her clan, so Qing went to greet the Alliance Leader first.

Spear Extreme Cao Xuanliang.

He was a figure respected by all spear users, regardless of Orthodox or Unorthodox factions, as the world's greatest spear user.

In fact, the perception of spears in Jianghu is particularly not good.

They say, why a spear when you're not a military general, swords and sabers can stab too, what's the point of spear techniques that only have the skill of stabbing, and so on.

And don't you have trouble coming up with titles?

Et cetera.

Because of this, there was a culture of spear users respecting each other regardless of Orthodox or Unorthodox tendencies.

In the midst of this, the world's greatest spear user made his name as the Wulin Alliance Leader, so of course he had to be respected.

Cao Xuanliang looked like a middle-aged man in his forties, young for a previous generation master.

But Master too, with her realm of Body Reconstruction, looks like a young mother when walking next to Qing.

Thanks to this, she understood he must be in the Profound Realm.

"Divine Maiden Sect outer disciple Ximen Qing greets Elder Spear Extreme. Though lacking, I have studied under Master Ximen Surin and am dedicating myself to the sword. I would be grateful if you could look kindly upon my still insufficient skills."

"Ho ho. I wondered what fairy-like child had come, but it wasn't that you lost your way from the celestial realm, but a little fairy from the Divine Maiden Sect. Yes. I am Cao Xuanliang. But, hmm. The Godmother didn't come?"

"Master said she regrettably couldn't attend because she was busy with sect matters."

"Is that so? Ho ho, that's unfortunate. The female martial artists of Wulin will be disappointed. Ho ho, ho ho ho, ho ho ho ho."

Somehow it was a hollow laugh but seemed to have sincerity in it.

In fact, Cao Xuanliang's face brightened.

"Yes, child. You still look young, but you're already at the end of the Peak Realm. How old are you this year?"

"This girl has reached the age of beauty in her prime years."

"You're really twenty? The Godmother has truly hit the jackpot with disciples in her later years. Wait… That's right! Crescent Moon Divine Sword! Right. Now I remember."

"Crescent Moon Divine Sword?"

Cao Xuanliang laughed seeing Qing's expression.

Saying her inner thoughts were all revealed by her expression, showing her transparent nature.

"You didn't know? The Mount Hua Sect Leader marveled that you were material for a divine sword like seeing the moon maiden, so the authority imbued in your title is different from the start."

\textit{What? I had a title? Crescent Moon Divine Sword?}

\textit{Ooh. Isn't that cool?}

Satisfaction settled on Qing's expression.

Cao Xuanliang laughed again at this.

"Ah. Right. You said outer disciple? Then that means there's no restriction on marriage. Do you perhaps have someone in mind now? Actually, compared to my great-grandson, it's a shame for the child, but this is the meddling of an old man."

"A lover? Right now I'm overwhelmed just training my skills, so I haven't set my heart on anyone else. And by that great-grandson, do you mean Young Master Cao Haocai?"

"Oh, have you met him?"

"I saw him from afar, but…"

Qing's expression became subtle.

At this, Cao Xuanliang's blood pressure also rose slightly.

"Ahem, yes. Although his conduct is a bit rash, he's not a bad kid at heart. And such a guy would give his liver and gall, no, all his internal organs to his woman."

"How can a man's fondness for women be a flaw. Hmm. Is it… a flaw?"

The Ximen Surin-style womanly act slipped slightly.

No matter what, she wondered if it was really right to cover up that behavior that came during her beggar disguise job.

"Oh my, it's all my fault. He showed signs from childhood, but I indulged him as my great-grandson and now it's just. I told my son to educate him, but he goes blind in front of his grandson. Then I should have at least urged my grandson. How well the family is going. We're about to have a Wulin criminal in the clan. If they say a sex fiend appeared in the thousand-year Jo clan, how can I face my ancestors when I die."

It was a sudden lament.

However, Qing, specialized in old people, didn't panic and said what he wanted to hear.

"Don't worry too much. From what I've heard, the men of the Dragon-Phoenix Assembly all agree in their evaluation that he's a very reliable and generous older brother, so it must be because his true nature is pure and magnanimous."

Of course, limited to when there are no women in the group.

Qing didn't bother to add unnecessary qualifications.

"Yes, that kid is good at heart. From childhood, he knew how to give to others and couldn't turn away from difficulties, so he's too good. Actually, that's why I'm worried. He's been scammed several times. No, does that make sense? How can the heir of the thousand-year Jo clan go around getting scammed? Just because someone looks a bit pitiful, he opens his money pouch first, not realizing that not everyone poor is a good person. I hope he finds a wise woman to firmly press down that light nature of his."

In fact, the Righteous Karma Qing saw in Cao Haocai was quite high.

"Elder, would you avoid helping for fear of being deceived? Even if nine out of ten people you save are lying, you're still saving one person. From what I've heard, that's what a great hero would do, so please don't worry too much."

"Yes! That's right! What truly grateful words! How can I- no, ahem. I really envy the Godmother. What could be more enviable than the blessing of children and disciples in one's later years…"

Originally, she heard she just had to give her name and leave, but suddenly the Alliance Leader's lament burst out, making the greeting longer.

Starting with worries about his great-grandson, then how the Wulin Alliance was running too slowly and not to his liking, and how the world was strange here and there with those demonic cult bastards and the Blood Cult doing this and that.

Others would have long since let go of work and leisurely wandered around training, but being tied to the Alliance and just clearing his throat and putting on airs, his fate in his later years was truly harsh.

Even his only joy was watching his great-granddaughter's antics, but now that she's grown up she just follows men around, that damn Jade Qilin, tsk tsk tsk.

To this, Qing picked out only the words he wanted to hear, giving him pleasure as refreshing as scratching an itchy back.

That's right. Qing's skill in old people specialization, old people slayer (the connotation is different from the Western language in Chinese) reached the heavens, so melting the heart of a lonely and busy old man was as easy as folding fingers.

"If I could match up my grandson, I'd have no regrets, but I wonder if that's something I shouldn't do to you. If it weren't for the Godmother, I would have adopted you as my daughter, but my heart is like that, so come visit often and be this old man's conversation partner. Is that alright?"

"Of course. Ah, but weren't there people waiting?"

"Right, that's how it is. What's the big deal about greetings that I have to sit solemnly all day watching people bow their heads. Right. Let's meet again next time. Go to the reception hall and say the Alliance Leader said to give you the Wucheon Pavilion, they'll give you lodgings."

"Yes, Elder. Thank you for your consideration."

"Being an old man's conversation partner is consideration, I'm just doing my duty. Yes, let's meet again."

And then as she left the Alliance Leader's reception room, the Peng family members were waiting sitting at a table outside.

She gave a slight bow to Daoist Gentleman Peng Xian whom she had met before, waved to Peng Daesan and Peng Chaolei, and then came out and asked a Wulin Alliance warrior for directions.

After going to the reception hall and relaying the Alliance Leader's words, she was guided to a tall building with the Wulin Alliance walls behind it.

As she entered the Wucheon Pavilion and climbed the stairs, as soon as she entered the sixth floor, the maid guiding her opened a door blocking the corridor and spoke:

"The honored guest can use this area."

It was a splendid corridor decorated with silk.

Seeing only eight visible rooms, Qing asked again.

"Can I choose any room? Can I look in all of them and choose? I'd like the biggest room if possible."

Then the maid smiled and answered.

"You can use them all. The entire sixth floor is the honored guest's lodgings. However, the servants attending to you and the honored guest are staying at the very end there, so if you need anything, please pull the signal cord attached to each bed."

"Oh?"

Qing opened her eyes wide.

\textit{What? I get to use a whole floor by myself?}

\textit{Hmm. Totally sweet.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Although she realized in one day that the Dragon-Phoenix Assembly wasn't much, didn't Ximen Surin specifically say to go to the Dragon-Phoenix Assembly and play with peers for a while?

It wasn't really saying to go play, but to go familiarize faces all around and exchange names, and Qing wasn't so dull as to not understand that much.

As Peng Daesan said, the banquet food had a difference in taste from freshly made new products at restaurants, so they were actually dishes that didn't matter if they cooled down or were meant to be served cold from the start.

"Hmm. I'll go today. Rest tomorrow."

There's nothing to do alone except sleep more anyway.

For now, I'll go to the Dragon-Phoenix Assembly today and make separate plans with friends, and tomorrow I should go see Zhongyuan's largest market that I still haven't fully explored.

\textit{I can go to a teahouse and eat and drink snacks while chatting}, she thought.
