\chapter{Dragon-Phoenix Assembly (10)}

\textit{I'm not sorry, but I do feel a bit sorry for her.}

Feeling the bitter aftertaste of alcohol, Qing was about to turn around to take care of Gong Sun-Yaoyi and return to her lodgings when:

"Gege Sister!"

"Ah! Isn't it Xiang'er?"

A tiny thing popped out and hugged Qing tightly, with the child's head pressing and rubbing against her upper abdomen.

She couldn't see it, but she felt it.

Since Qing couldn't see, the same was true for the child.

"Oh. I can't see Gege Sister…"

"Xiang'er. There are things you can't see when you're too close. Would you step back a bit?"

When Zhuge Xiang stepped back, the child's face was revealed.

"I thought our Xiang'er looked even prettier today, so you put on makeup? But if you didn't want to wear makeup, you should have said so instead of wiping it on your robe."

"Hup."

"Oh dear, it's smeared."

When it comes to makeup in Zhongyuan, the name of Xi Shi, the most beautiful woman of all time, pops up again and again.

Xi Shi's frowning face has become ingrained in Zhongyuan people's psyche, a strange obsession with sad faces.

So they lightly painted the area around the eyes red on a pale face to create the flushed color of a woman who has been crying.

Other than that, eyebrows and lips were up to the person doing the makeup.

They would slightly draw the start of the eyebrows towards the forehead to create a frowning look, or paint only the center of the lips red in a cherry shape.

Zhuge Xiang's eyes were smeared red on both sides, clearly having drawn a line on the upper abdomen of her robe.

The white powder was probably extra.

Qing smiled brightly at Zhuge Xiang, who looked fidgety after making a mistake.

The child, whose smile spread with the sound of laughter, spread both arms wide.

"Gege sister, hug me."

"Oh my, how cute."

Qing picked up the child and scanned the surroundings.

Zhuge Xiang wouldn't be alone, ah. There he comes.

"Sister, I'm sorry. Xiang'er seems to be especially fond of you. She was already making a fuss about wanting to see you, and now this. Xiang'er, you shouldn't act spoiled with sister in a place like this."

"No, no. It's fine. I was just thinking I missed Xiang'er earlier, hmm? How did I come to miss her? Well. Anyway. The important thing is that she's here when I missed her, right?"

"That's right!"

"By the way, what's all this commotion?"

"Yeah. What is all this commotion."

It wasn't something the person involved should say, but.

Since Qing hadn't planned it, she had just gone along with the scheme after drinking alcohol on the seventh floor.

"Sister, sister, I want to eat peaches."

"Now you're ordering me around like a servant? If this wasn't so cute, really. Well, shall we go look for peaches?"

Since all the tables on the first floor had been cleared away, they had to go up to find peaches.

As Qing climbed the stairs, the other beauty from the seventh floor earlier came down click-clacking and passed by without even glancing at Qing.

The difference from earlier was that now Qing had two Zhuges attached to her.

"Who was that beautiful woman who just passed by? How should I put it, she's pretty? Hmm. Pretty."

"Are you referring to Miss Seol Iri, the Ice Snow Flower?"

"Ah. It doesn't have to be four characters?"

"If we added to it, it would be Cold Ice or Freezing Ice, but it doesn't sound good, so. She's staying at the Wulin Alliance as a guest of the Ice Palace for about five years now."

"Hmm. I wonder if there's a way to become friends."

"Even with your dog-like friendliness that makes you the friend of humans, sister, it would be difficult to become friends with Snow Flower. She hasn't interacted with anyone for five years, so she just wants to be alone."

"Hmm. There are people like that too. But, Zhuge. Dogs are man's best friend. And dogs also bite people. Do I really have to act like a dog? This is getting more and more cheeky?"

"Haha. Sister. Aren't your arms sealed right now? If I don't act up now, when can I- guk."

Zhuge Lixian, who was precisely hit on the tailbone, rubbed his buttocks and bounced kwoong kwoong.

The giant, a span taller than Qing, bouncing made the stairs vibrate and shake.

Zhuge Xiang laughed happily at the sight.

Qing bent her outstretched leg at the knee and stood on two feet on the stairs again, saying:

"If you want to seal me, bring two more Xiang'ers. If you hang one on each leg, then you could say I'm truly sealed."

"Ung. There's no child in the world as cute as Xiang'er."

"Then. The sealing is ruined too."

"How do you kick so accurately at the crotch even when kicking? Even for me, it hurts when you hit the bone."

"Isn't your butt just full of muscle anyway? Kicking it would only hurt me."

"Well, um. Muscle. Right. About what you said when you visited that time. Perhaps at the Unrivaled National Instructor's training ground…"

That's when it happened.

As soon as they finished climbing the stairs, someone came to greet them, cutting off Zhuge Lixian's words.

"Oh! Who do we have here! The honorable winner of the drinking contest! Hahah, I saw it well."

"Oh, Brother Cao."

"Oho. The young lady already knows me. That's right, I am Brother Cao, Cao Haocai."

The great-grandson of the Wulin Alliance Leader and heir to the Black Dragon Cao Clan, and affectionately called 'that bastard crazy about women' by the Heavenly Martial Team members.

Qing flinched for a moment.

\textit{Come to think of it, wasn't I wearing this same face veil when I saw him? Should I cover my mouth?}

But it was an unnecessary worry.

The face veil of the flower beggar Cao Haocai saw was so dirty and tattered, it was completely filthy, looking like it might fall apart.

However, it was clean now.

Even Peng Daesan had asked if it was originally that color, so how could he connect the two when looking at a national treasure-grade face veil that should be presented to a princess?

"I think you're mistaken, young master. I lost the drinking contest."

"Who would think that? Rather, I was deeply impressed by the magnanimity you showed. Indeed, no matter what anyone says, isn't a silky heart the most important thing in a woman?"

Qing's eyebrow twitched.

This guy, what's he up to?

"I've heard that Young Master Cao is quite fond of women. Excuse me, but do you perhaps not have a lover?"

"That's right. This Cao Haocai is still a man who hasn't dated, waiting for his soulmate. But why do you ask that…"

"No particular reason. You just seemed that way."

At this, giggles burst out.

Right behind Cao Haocai's back.

"Brother, that's why you get cursed at when you talk like that. What idiot in the world compliments a woman's heart?"

"Oh. Is that not okay?"

"Why. You should go crazy if she's ugly. Ah, sorry. I didn't mean to hurt Miss Ximen's feelings…"

"No, it's fine. I don't care about that kind of thing."

It's when you tell an ugly person they're ugly that it scratches their heart.

Qing knew she was a beauty to the point of being startled when she looked in the mirror, so she could just giggle and let it slide when someone said she was ugly.

"I'm Cao Yangyang. Um, I've been on the seventh floor yesterday and today, and after seeing you verbally destroy people, I decided to respect you. Is that okay?"

"Well, that's up to you, isn't it?"

At this, Cao Yangyang's expression bloomed.

In fact, when women say they've decided to respect you, it means they want to join your faction.

Similar expressions include "you're so pretty I want to call you sister" or "I want to do your makeup," indirectly conveying a desire to be close while praising something.

But how would Qing know?

"Respect? Of course, I have so many respectable aspects that it would be tiring to list them all, but I don't think I showed any good sides yesterday and today on the seventh floor."

"No! I've been told I have a bit of a foul mouth. That's because the men in Heilongjiang are bastards who need to be cursed at to even pretend to understand, so it's unavoidable, um, it's not an excuse but really. Women on our side are like this."

"It's true, sister. Heilongjiang women are famous for being the most foul-mouthed in Zhongyuan-"

"Zhuge, turn off the commentary. If Heilongjiang men are like Brother Cao, I understand. So?"

"Seeing you verbally destroy people gently yesterday and today, I realized you can do that without using vulgar words. Actually, because my speech is so terrible, I can't open my mouth anywhere. I feel like I'll die of embarrassment. They call me a bitch with a rag in her mouth, so I always sit at the bottom and can't even speak."

"Hmm. Actually, I'm not naturally good with words either. I'm like this now because there are people around, otherwise I can hold my own too?"

In fact, it's not just holding her own.

Qing was Zhongyuan's top expert in cursing.

Wasn't she the owner of the formless, poisonous tongue of death that even impressed the Grand Elder of the Tang Clan?

"That's right! Sister's eloquence always surprises and thrills even this fool, every moment inspiring respect with its novelty, truly deserving to be called the best under heaven."

Zhuge Lixian agreed with exaggerated enthusiasm.

Qing smiled and said:

"My master put a lot of effort into it. Hmm. Yes. If you stay at the Divine Maiden Sect for one season, you can become like this. If you're really desperate, I could speak to my master-"

"Ah! Please!"

"If that's really your wish."

Qing smiled with satisfaction and mourned in advance.

\textit{Because Master's education comes with pain.}

\textit{That good thing, I can't be the only one to suffer it.}

While this was happening, someone else approached.

"Miss Ximen! Are you alright? You seemed to have drunk too much. Here, have some rock honey."

"Oh my, I don't have hands right now."

This time it was Gong Sun-Tianri, Gong Sun-Yaoyi's burdensome brother.

At this, Cao Haocai's eyes, which had been sad but kind, suddenly turned like those of a fierce beast.

Hmm. So that's what it is.

When there's only a woman in the group, seeing all men as enemies.

The Gong guy kept saying greasy things every time he opened his mouth, and Cao Haocai gritted his teeth each time, occasionally interjecting with obvious remarks only to get cursed at by Cao Yangyang.

Gong Sun-Tianri's level in seducing women was so high that Cao Haocai was no match at all.

"Gege sister. That peach…"

"Ah. Right. I forgot because of these people. Yes, let's go find peaches. Now, where are the peaches\~"

"Where are the peaches\~"

Zhuge Xiang sang along with Qing's humming about finding peaches.

\textit{Why is she so cute? It's no joke.}

While playing with Zhuge Xiang like this, three men followed behind.

Aish, what is this picture?

Your voice is truly beautiful, your hands are so beautiful, the way you play with children is so beautiful, no Jo hyung this bastard is going crazy saying everything is beautiful?

Qing, who had become beautiful in everything except her face, decided she should just avoid Cao Haocai if she saw him.

Compared to that, saying you should eat in advance to suffer less from hangovers, finding peaches and sticking them on skewers to give to Zhuge Xiang.

Although burdensome, the Gong brother who was busy taking care of various things was better.

Finally, unable to bear it anymore, Qing promised Zhuge Xiang to come play at the top of the Wucheon Pavilion next time and left.

Gong Sun-Yaoyi's brother carried her, sleeping obliviously, and loaded her onto the carriage.

"Please take good care of my sister. She's a shut-in who's stubbornly stuck and won't bend. Haah."

'Foolish idiot bitch', the muttering hidden after the sigh was caught by Qing's hearing.

But despite his words, concern leaked out through his eyes, so he was a brother who took care of his sister no matter what.

At this, Qing made a sound like air leaking.