\chapter{Dragon-Phoenix Assembly (8)}

Although Murong Zhuji asked for a reconciliatory drink, she didn't expect Qing to accept without even a moment's hesitation.

She naturally thought she would be refused.

Of course, if she was refused, just saying 'Oh, you're avoiding it. Well, can't be helped' and giving up would just make her a fool.

She had prepared various means to gently persuade and melt her if refused, so all her efforts of planning for various scenarios last night were in vain.

\textit{What's this? Was my acting too good?}

\textit{Or is her head full of flowers so she really thinks I'm asking for reconciliation?}

However, after hearing a loud gulping sound, Murong Zhuji realized the reason.

\textit{Ah, this bitch. She's crazy about alcohol.}

\textit{Right, so you can drink quite a bit?}

\textit{You're not refusing because you're confident you can beat me with alcohol?}

But Murong Zhuji was also a drinker who had never been defeated from her first drinking session in life until now.

Yet Murong Zhuji never overestimated her drinking capacity, being as cautious as the size of her grudge.

Besides that, she had prepared a secret weapon, so it was a fight she absolutely couldn't lose.

"Does Miss Ximen enjoy alcohol?"

"Yes. I drink as much as I can get."

"Ah. Then since you've come to Henan Province, do you know the alcohol that comes to mind with Henan?"

"Ah. Could it be. Dugang wine?"

"You know! I prepared a special alcohol as a gesture of reconciliation, it's called Xijing Dugang wine made with water from the Xi River."

"Xijing Dugang wine!"

Qing shouted without realizing, and then had a great realization.

\textit{Ah. So this is why everyone shouts when titles come out, it's just fired automatically without thinking about it.}

When Murong Zhuji gestured, a woman appeared carrying wine bottles and cups.

"Here, I'm buying the alcohol, not the Dragon-Phoenix Assembly. Take the first cup. Come on."

The cups for strong liquor are so small they hold just two spoonfuls, and even then they're only half filled, so it's really just one spoonful.

It was just a swirling spoonful of white liquor, but its clear fragrance already filled the surroundings, exploding and blooming.

"Hiya, it smells good just sniffing it. Miss Murong, you take a cup too."

Qing poured alcohol for Murong Zhuji, who received the Dugang wine in her cup and returned to her seat.

The table was so large that the two sitting opposite were at the farthest distance on the circle.

And then as Qing was about to pour alcohol for Gong Sun-Yaoyi, she asked just in case.

"Wait, Yi. Have you ever drunk alcohol before?"

"No… But I want to try."

…with a friend, the muttering to herself was clear to Qing's sensitive ears.

Feeling sorry for her again, Qing explained simple drinking etiquette playfully, like an adult giving a child a spoonful of alcohol.

"Really? Originally, you're supposed to empty the first cup at a drinking session in one go without leaving any, okay? That's why it's called ‘dry cup'. Dry. Cup. But this is a bit strong. For now, just this much."

Qing skillfully tilted the bottle and dropped exactly four drops, tok tok tok tok.

"Is it this little?"

"You'll think differently even after drinking that much? Come on, let's toast. To friendship."

Qing raised her cup to eye level and then downed it in one go.

Cold fire goes down.

The fragrance of the alcohol passing through the esophagus leaks into the airway and is exhaled through the nose.

Not just the fragrance, but it feels like the alcohol spirit is mixed in the breath, so all organs above the solar plexus and below the eyes heat up at once.

Qing unknowingly let out an excited sigh.

"Haaa… this is it."

"Kheuk, cough! Cough!"

As expected, violent coughing sounds came from the side.

Qing gently rubbed Gong Sun-Yaoyi's back.

"Yi, are you okay? See, it's not easy, right?"

"My stomach… is burning. Is it, is it poison?"

"How could there be such a fragrant poison? The scent is really nice, right?"

"Mm, the scent, is really nice. Is the burning stomach, normally like this? But, it's too bitter. It doesn't seem to taste good."

"You say alcohol doesn't taste good? I think it tastes better than real drinks."

"Eh, Miss Ximen too. You're teasing me, right?"

"It's because Ye doesn't have the constitution for it. Since I have a good constitution, it just tastes like sweet fruit tea. The fragrance. Wow, the fragrance is really. I want to see the fragrance."

"…?"

Qing said whatever came to mind while filling Gong Sun-Yaoyi's cup, and then explained simple drinking etiquette.

"Just close your lips tightly and lightly touch only the middle, then drink as if you're just lightly wiping your wet lips. It's strong alcohol, so absolutely don't let it flow into your mouth. If you feel it doesn't suit you, don't drink. It's better than making mistakes while drunk."

As Qing was saying this to Gong Sun-Yaoyi, she had a realization.

Ah, so Murong Zhuji is determined to send me off with alcohol now?

But to me, who's at a level where alcohol and water are indistinguishable? Such a novice.

As expected, Murong Zhuji said:

"Ah, Namah. Since it's far to pour every time, you pay special attention to make sure Miss Ximen's cup doesn't empty. Understand?"

"Yes. I understand. Miss Ximen, you won't feel slighted if I pour for you, right?"

The words "pay special attention" meant absolutely not letting the cup be empty.

And she probably can't stand seeing my cup full either.

But to Qing, alcohol was just a drink that made her feel good no matter how much she drank, enjoying the fragrance and heat.

Qing went one step further.

"Why would I feel slighted? But, isn't my cup empty now? Aren't you going to fill it?"

Seeing this, Murong Zhuji smiled a sinister smile.

In fact, although the bottles were the same, the contents were different.

The bottles placed around Qing contained Xijing Dugang wine, famous for being the strongest in Henan, while the bottle next to Murong Zhuji wasn't actually a wine bottle but a tea bottle containing tea.

As soon as Qing's cup was filled, Murong Zhuji spoke as if she had been waiting:

"Come on, Miss Ximen. Let's play without leaving out us women who enjoy alcohol. Come on."

"Oh my, will you be alright? I'm a bit of a heavy drinker, so you might run out of alcohol?"

And so one cup.

"Then, this time Jeonga will say something?"

Two cups, three cups, four cups…

"Then after one round. Miss Ximen, please say something again."

And so one bottle, and two bottles…

In an instant, five bottles disappeared completely.

"Hmm. Ah, feels good."

Qing swayed left and right, humming a tune.

It was a deliberate act of pretending to be drunk.

Although the ploy was petty, it was effectively getting unlimited expensive alcohol bought for her, so shouldn't she play along a bit to keep the sponsor excited?

Pretending to be drunk is a skill shared by all Koreans in Qing's homeland, to the extent that it's taught as part of the regular curriculum in schools from a young age.

"Heheh, Miss Ximen."

"Yes? What is it?"

"Nothing. I just wanted to call you. Miss Ximen. Miss Ximen. Mmm. Qing'er. Huaaa, I can't do it. I'm embarrassed."

Gong Sun-Yaoyi raised her cup and downed it in one go.

Qing clicked her tongue at the action that mimicked her own.

\textit{Strange? I clearly told her to just wet her lips?}

"Who gave Yi alcohol?"

"Ah, she kept asking for it…"

"How much did you give her?"

"About one and a half bottles…"

The woman next to Gong Sun-Yaoyi answered hesitantly.

While Qing was busy pouring alcohol, Gong Sun-Yaoyi had been sipping little by little, gradually coming to like it and drinking more and more.

"She drank quite a lot. Yi, are you okay?"

"Yes. I feel good. Good. But how can Miss Ximen drink so much? Drink? I feel strange, ah! This must be what being drunk is. I'm drunk. Heheh."

Gong Sun-Yaoyi said this and tilted her head, then looked at Qing again with an unfamiliar loose smile and said:

"But I feel good. Good. But how can Miss Ximen drink so much? Drink? I feel strange. Ah! This is-"

"Yi was an infinite loop type."

"Infinite loop? What's that? What is it. But I like Miss Ximen. My friend. First friend. Only precious friend. But."

And then she tightly hugged Qing's arm.

"But it's unfair. Fair. I only have Miss Ximen as a friend, but Miss Ximen has too many. That's not right. I'm giving all my heart, but Miss Ximen is dividing hers. Dividing. I don't like it. Can't I be more special? I want the biggest piece even if it's divided. Because, it's unfair. I only have a friend-"

"Couldn't Yi just make lots of friends too?"

Qing tried to break the repetition first.

Then a heavy voice popped out.

"Everyone hates me. Before Miss Ximen became my friend, I was alone for half a month. I was alone. No one talked to me. Men, I thought men were friends but they weren't. They're not. They said if they coax the stiff bitch a bit she'll probably put out. It hurt so much. It hurts. So much."

"What bastard is that? He should know today's the day his head gets cracked open. Who is it? Just tell me."

"Heheh, are you getting angry for me? Angry? As expected, I only have Miss Ximen. But it's unfair. Fair? I only have Miss Ximen as a friend, but Miss Ximen has too many, so it's unfair, this shouldn't be. It's bad. I'm giving all my heart, but- yawn. I'm sleepy. Sleepy. I want to sleep. Sleep."

And then the head leaning on her shoulder felt heavy, and then lost strength and spilled onto Qing's lap.

"Oh dear."

Qing looked at the women with a troubled expression.

"I heard the sixth floor is used as a rest area, is there perhaps a place where she can lie down?"

Murong Zhuji answered after a moment's thought.

After all, her target was Ximen Qing, not that foul-mouthed Gong clan girl.

"There should be a room with paper walls. It says Women's Rest Area."

"I'll just go lay my friend down for a bit and come back."

As Qing lifted Gong Sun-Yaoyi and disappeared down the stairs, Murong Zhuji let out a suspicious breath.

\textit{Is she really drunk?}

\textit{She suddenly looks fine?}

But that was only for a while.

After laying Gong Sun-Yaoyi down and even giving silver to the rest area maid, asking her to take special care of her, Qing tripped on the last step of the stairs and fell flat.

\textit{Ah. She is drunk!}

\textit{It must be a type of drunkenness that doesn't show outwardly!}

Murong Zhuji ran over with a broad smile, pretending to be worried.

"Oh my!!! Miss Ximen!!! Are you alright!? To fall like this!!"

Qing's eyes narrowed.

\textit{This bitch is really determined to humiliate me.}

\textit{I pretended to be drunk but it seemed in vain because I took Gong Sun-Yaoyi away, so I fell once, and wow, look at that expression not even managing her face saying it's a drunk person.}

\textit{She's really excited.}

"Ah. I'm fine."

"You don't seem fine? It was just five bottles, only five bottles? You acted like you loved alcohol so much, but five bottles, heh, five bottles, you shouldn't say you can drink anywhere. Falling like this after just five bottles."

\textit{Now that I look, it seems she's deliberately not managing her expression.}

\textit{Because it was a provocation that no drinker could ignore.}

\textit{Is she pulling this petty trick?}

\textit{Should I make her drink more? Alright. I'll play along once.}

\textit{But what's with her? She's fine after downing five bottles? Was she also born choosing to be a Blood Poison Human?}

"What you just said, I can't let it slide. This Ximen Qing has never lost in drinking anywhere."

"Oh my. Me neither. Then shall we see who is the greatest drinker of the Dragon-Phoenix Assembly in front of everyone this time?"

"That's what I should be saying. Alright. Miss Murong, will you be crawling home today?"

"Well, I wonder who will end up crawling like a dog? Girls, did you hear? Miss Ximen has challenged me to a drinking contest, so we should accept it. Right? Go downstairs and tell them to prepare."

It was a cunning speech subtly pushing Qing as the one who challenged to a contest.

Qing inwardly clicked her tongue.

\textit{Wow, not just anyone can be a leader}, she thought.

"Come on, get up. It will take some time to prepare, should we drink more in the meantime? Surely, you won't avoid it because of the contest?"

However, playing along is playing along, and being annoyed is being annoyed.

Qing reached out her hand from her fallen position.

When Murong Zhuji grabbed that hand and pulled, Qing exerted force and threw her.

Bang! Murong Zhuji, who was off guard, was thrown to the floor without time to react to the terrifying force.