\chapter{Dragon-Phoenix Assembly (4)}

Murong Zhuji could only open and close her mouth.

It felt like boiling water of rage and shame had filled up to her throat, so she couldn't make a sound for fear that hot liquid might spurt out instead of words.

All she could do was struggle not to make choked sounds from the heat filling her lungs.

"You, hic, dare…, huk…"

Not only was the Murong kid small, but his sister was also petite and thin, so her body was small and her face only as big as a palm, with unusually large eyes now filled with dangling teardrops.

Seeing that sight, Qing felt a pang of sympathy and wondered if she had gone too far.

But insulting the Divine Maiden Sect robes clearly crossed a line.

Although they were robes personally made by her master for a disciple with long limbs and a thicker body than other women, above all, all Divine Maiden Sect disciples wore the same style of clothing.

What poor clothing, what appearance, she had started to say, but even without hearing the rest, one could guess what would follow.

It was like insulting the entire Divine Maiden Sect, so it was a great rudeness that Qing couldn't overlook.

"Miss Murong, you should be careful with your words. Although the Divine Maiden Sect may not be a very famous orthodox sect like the Nine Sects One Union, none of those people would dare say ‘how dare you' to a Divine Maiden Sect disciple."

In fact, it wasn't because the Divine Maiden Sect was prosperous, but because of the existence of Ximen Surin, the Zenith Among Women.

It was Ximen Surin's disciples who had high rank, not that they were respected as elders of the Divine Maiden Sect.

Even among Daoist sects there are ranks, and the Divine Maiden Sect was actually just a small to medium-sized Daoist temple far below orthodox Daoist sects like the Four Direction Sword Sect that Mount Heng Sect belongs to, or Mount Mo Sect and Mount Qing Sect.

It was widely known as a mysterious sect of women, but in other words, there was nothing left if you took away the mysterious sect of women aspect.

"You, aren't you being too harsh!"

"That's right, you're too much!"

Feeling sorry for their trembling leader, Murong Zhuji's group came to her defense.

In fact, Qing's words didn't sound like someone else's, so they were angry and sad together, and the sight of them huddling together to comfort her was quite touching in its closeness.

"Zhuji, it's okay. We're here for you."

"That's the level of big-breasted bitches' humanity. They don't even see you as a woman just because you don't have any. You know? We only have each other."

"Hic, huk…"

Amid the warm comfort, Murong Zhuji finally burst into tears.

In fact, offering comfort at times like this is not much different from slapping someone's cheek telling them to cry.

It's like pouring dry leaves on an ember.

Qing scratched her head.

\textit{Ah, she's crying here.}

From what Qing had observed before entering Jianghu, women's power struggles were scored by combining two aspects.

One. Who can deliver more backhanded insults.

The most important subtlety in women's verbal battles is not to attack directly.

You have to exercise the way of indirection, making it seem like you're saying it out of concern for them, making them look strange if they get angry.

According to some law, in this kind of backhanded insult battle, the first person to get angry is considered the loser.

And two. Who is the more pitiful woman?

Or who is more of a victim?

In fact, the battle corresponding to the first aspect was as common as breathing in women's society.

That's why greetings and attacks were indistinguishable, roughly like this:

‘Hey so-and-so, hello? Wow, what? New outfit? You look so pretty today. Are you going to that trendy bar again? I'm not really into those places. You know, with men coming up to talk and all.'

This was the basic process of war, gathering allies by saying I don't get along with that bitch, and also specifying the enemy.

If you're not careful at this point, you'll be branded a bat and become a fucking bitch attacked by both sides before the war even starts, so you need to gauge the forces well and join the side with higher odds of winning.

The real war was a total war, the competition of who is the more pitiful woman corresponding to the second aspect.

This was a contest of who was the more pitiful person as a victim, so bursting into tears at the right moment was the most important high ground.

If you cry too abruptly, you'll be criticized for crying forcefully, asking what you did right to be whining, and your defeat will be confirmed at that moment.

So at a moment when everyone thinks ah that was a bit harsh, hmm that crossed a line, bam! Tears flow!

However, according to some law, the moment one side bursts into tears, a strict judging panel makes a decision, so you need to be careful.

Just like now.

'She's always picking fights, but why is she crying so well?'

'Ha, I knew that bitch would get what's coming to her someday for messing with the wrong person.'

'Always saying others are vulgar and exposing everything, saying they're obsessed with men and look lewd, but she's the first to flirt when the Jade Qilin appears.'

This was why people showed unusually kind behavior before the total war, emphasizing their goodness in front of the judges.

A sudden stamina potion could be the prelude to war.

Because if you cry but don't get sympathy, you'll just end up looking ridiculous.

Qing, a master of tightrope walking, read that atmosphere.

"Oh no, miss, I'm really sorry. It's because these robes were personally made by my master and are very precious to me. When you said even beggars wouldn't wear such dirty rags, that it was a poorly sewn mess wasting good fabric, I got a bit upset. Will you please forgive me?"

Chen Sui, who was listening, felt a chill down her spine.

\textit{Wow, Sword Flower didn't even say anything that harsh.}

Murong Zhuji also snapped back to her senses.

It was the ‘my mom made this for me' attack.

If you don't get your act together, you'll end up being the bad bitch who even insulted someone else's family.

"Th-that, I. I wasn't criticizing…"

And then everything went black.

If she said she didn't insult that harshly, wouldn't that be admitting that she did insult to some extent?

"Looking closely, the fabric is really high quality, hic, it's an excellent robe with such care put into it, huk. I made a mistake because I saw wrong."

"Ah. A mistake. Anyone in the world can make mistakes. I'm really sorry. I didn't know that. I'm so sorry. I was wrong. Since we both made mistakes, how about we forget about it?"

"Yes…"

"Everyone, you heard that, right? You didn't hear anything either, right?"

Chen Sui felt a bit of regret.

\textit{Wow, she's letting it go here.}

\textit{She could have just driven her out so she couldn't even set foot in the Dragon-Phoenix Assembly during the Wulin Conference.}

Qing didn't need to make more enemies unnecessarily, and thought this was enough for Murong Jun's sake.

"Oh my, it seems the atmosphere has become a mess because of me. I think I should leave for a while. Miss Chen, I'll see you next time?"

"Ah! Yes! Take care on your way."

\textit{And she even offered to leave first.}

\textit{Not knowing what gossip might come out, she said she'd leave without solidifying the situation, showing the magnanimity of a generous victor.}

On the landing of the stairs going down, Tang Lan-Ah said:

"But, it's almost pitiful. Wasn't that too harsh? Now you're completely enemies."

"I thought she just didn't get along with Miss Chen, but seeing how she treated me, it seems she picks fights with anyone with big breasts. Thinking about how she'll keep grating on my nerves in the future, I needed to establish some discipline in advance."

This was why Qing deliberately poured out harsh words and beat her down hard.

That type, if left alone, gets more and more arrogant and crosses the line increasingly.

It's the type that grows festering hatred, with what others have sticking in their heart like a thorn because they don't have it themselves.

It was a lesson Qing had learned from experience.

Before entering Jianghu, Qing drove the best-selling domestic mid-size car in her homeland.

Her uncle, whose land value had increased, bought a foreign car, and her cousins made spoiled complaints saying they'd never ride in uncle's car, especially an old model, so it ended up coming to Qing.

Sweet deal.

But there were quite a few people who had fits seeing a young production worker driving a mid-size car.

Among them was a particularly severe Mr. Park-

'You must be earning well? Young people these days don't save, just live for today? It must be nice driving a good car, picking up women?'

Qing endured it because he was an elder.

But as it kept getting worse, she finally started pouring out ten paragraphs of car boasting every time he mocked her with such words.

'Wow, yes. It's really good. You wouldn't know because you haven't driven it. You should get one sometime. It's a full-size car so the ride quality is completely different, when I drive other cars it's so shaky I can't drive. Haha, it's called reverse perception, right? Don't do things like test drives, the reverse perception is really big.'

In the end, when he had a major explosion starting with ‘You little bastard', she immediately reported it to the HR manager and got it resolved.

After that, people picking fights completely disappeared.

"""Elder, you've come."""

As they came down to the fifth floor again, the Daoist youths awkwardly stood up to show respect, and Qing said with an embarrassed look:

"You don't need to be so formal. I'm just a young girl, so please treat me comfortably?"

At this, the expressions of the young Daoist martial artists also relaxed as if relieved.

In fact, there's nothing more unpleasant than a young person acting arrogant because of high rank, so it was common to treat them as a difficult younger sibling with reversed honorifics.

However, the lower-ranked person can't say ‘you're young so let's be friends', so if Qing didn't bring it up, they had no choice but to treat her as an elder.

"Hmm, Sword Friend. Looking at it this way, a Daoist was a Daoist after all. Brother Changbin seems to have trouble distinguishing whether it's because Sword Brother is a woman or because of rank."

"It's probably both for Changbin. Changbin, how about it?"

"Ahem, for me the young lady is an elder. I don't know much about women being difficult."

\textit{He seems a bit more comfortable since we traveled together?}

In fact, it was closer to him becoming comfortable because Qing had shown such a manly disposition, but how could Qing know Changbin's inner thoughts?

Qing smiled wickedly and pushed forward Gong Sun-Yaoyi.

"Ah, this is Miss Gong. This is Changbin, the Plum Blossom Swordsman of Mount Hua."

"So you're the great expert Changbin of the Drunken Demon-Subduing Sword. I've long heard of your reputation. As a fellow swordsman, it's truly an honor to meet you like this. Would you someday share swords and bestow your precious teachings?"

"……"

At Gong Sun-Yaoyi's polite praise, Changbin's face turned bright red and he just nodded.

"Oh! The young lady's words are truly excellent. Yes, as swordsmen, it's only right to greet each other and compete to improve our skills! As expected, even Sword Friend's companions are extraordinary!"

"That's because it's Sword Friend."

Qing nodded her head.

Ignoring Tang Lan-Ah's muttering of ‘Then what am I', Qing made introductions again.

"Yes, this is Nan-gong Shencai, the Young Sword King. His realm is a bit low for a Young Sword King, but his passion for swords is unmatched in all Zhongyuan, yes, he's truly a passionate swordsman."

"Passionate swordsman! How beautiful! I must change my title from today. Isn't it a much sweeter expression than Young Sword King! How is it that every sound coming from Sword Friend's mouth strikes the heartstrings!"

"Hmm."

Because Nan-gong Shencai shouted so loudly, Gong Sun-Yaoyi missed her chance to speak.

"I've looked around, but the Dragon-Phoenix Assembly isn't to my taste. It's better to move my body at least. Sword Friend, shall we spar after a long time?"

"I was about to say that. I found it difficult to bring up because Sword Friend was acting like a woman, but indeed, Sword Brother, this is the relationship of those connected by the sword! Come, let's go! I have many newly carved wooden swords."

"You brought wooden swords?"

"Of course I brought them. Isn't it common sense? I left them with a servant. They should be resting at the teahouse just ahead, I'll go fetch them right away."

And with that, he ran off excitedly, disappearing down the stairs in a flash.