\chapter{Dragon-Phoenix Assembly (15)}

Qing burst out laughing.

It seems she had complained to her brother.

"Why, what did she say?"

"She said some woman suddenly picked a fight and humiliated her in front of people. She even said she was hit and it hurt."

"Oh? Hit? Where was she hit?"

"I don't know that."

Tang Lan-Ah made a sound of being at a loss for words.

Then she spoke as if it was ridiculous:

"Is she now lying to her brother too? Hey. Picking fights and humiliating people is what your sister usually does, you know? Your sister picks fights with anyone who catches her eye. Well, not exactly, but more or less."

"Our sister does?"

"Yeah. Everyone just lets it slide saying ‘poor thing' so now she thinks it's okay to just do it. She just got a taste of her own medicine for messing with the wrong person, that's all."

Murong Jun's eyes trembled.

"Is it, is it true? Sister Qing, is what Sister Tang said true? Our sister…"

"Hmm. From what I've seen, she was that kind of person. San, do you perhaps know?"

"I don't know. I'm not interested. I just thought she was a bit of an annoying woman."

"No slipping away, okay?"

Qing poked Peng Daesan's side, then hugged Murong Jun, who had fallen into confusion after learning the truth about his sister, and said:

"Even if Jun's sister is that kind of person, Jun should take her side because she's family. Don't make an expression like ‘How could this be?'"

"Ah! Yes!"

"Qing'er is really, her kindness, I'm touched."

As Tang Lan-Ah chimed in, Peng Daesan clicked his tongue.

"You're teaching the child such good things. Shouldn't you rather speak more harshly to family?"

"That's for when they've done something really wrong. Well, if they've vouched for someone, you might need to break their legs to teach them a lesson. But for small things, isn't it right to take their side?"

"That's right. Qing'er is right."

"Don't small things accumulate to become habits?"

"Hmph, hmph."

"Small things accumulate to make people feel hurt. Anyway, people who feel wronged won't listen even if you tell them the right thing, right? If even family says it's your fault for just having an argument and being embarrassed, it only makes them feel more miserable."

"That's right, that's right. Everything Qing'er says is right."

"…Isn't the result of such indulgence right next to you?"

"What!? You want to try me?"

Tang Lan-Ah lit up with anger and stuck her hand into her bosom.

Qing shook her head and said:

"Lan-Ah. Put the poison away. Use words. Words."

"Kuk. What a waste…"

"San, be careful too. She really uses poison."

"Hmm. You're talking as if our dog bites."

At this, Tang Lan-Ah growled.

"Ha, you think I can't bite? You'd better get away from Qing'er before you really get bitten. No, I'll bite you when I get the chance, so just be prepared. Hmph."

Qing thought as she watched this.

\textit{Hmm. She definitely has something dog-like, something like a pet dog feeling.}

In fact, the physiques of martial arts clans tended to show distinct characteristics for each family.

You could call it genetics.

Training in martial arts from childhood creates an ideal body suited to it.

And in long-established martial arts clans, such bodies are passed down for generations, gradually becoming solidified as characteristics.

For example, burly physiques are rare in the Zhuge clan. Zhuge Lixian is a very unusual case, but they generally don't build muscle or even fat easily, and their skin has a sickly color.

The Hebei Peng clan, due to handling long sabers, are tall but not thick, though their muscles are dense and defined.

The Hwangbo clan pursues heavy weapons and fist techniques, so they have large, thick bodies, while the Black Dragon Jo clan just has healthy brown skin because of their foreign origin.

In the case of the Murong clan, their characteristics were not tall height, thin upper body and strong lower body.

This was a physique suited to the dual swords that pursue extreme speed, which the Murong clan's martial arts aim for.

Murong Zhuji had just inherited that direct lineage blood very thickly, among the thickest, really too too thickly.

So Murong Zhuji had long ago given up on her chest.

It's not that there aren't fairy arts that cultivate a voluptuous female body, but they have a yin nature.

It's completely opposite to the yang-focused Divine Arts Murong Zhuji learned, so she would have to completely scatter her Inner Qi to learn it.

She couldn't give up her clan's martial arts, so there was only one hope left.

Reaching the Transcendent Realm and achieving Body Reconstruction.

This was also the reason why Murong Zhuji was surprisingly evaluated as being serious about swords.

Thus, there were two things Murong Zhuji wanted so desperately in the world: one was a voluptuous, or at least modest, chest.

And the other was, as all daughters of martial arts clans desire, the heart of the world's most handsome man, the Jade Qilin.

And Murong Zhuji had rushed over at the news that Peng Daesan had appeared at the Dragon-Phoenix Assembly, which was a very rare occurrence.

And then she heard news like a bolt from the blue.

News that she had lost both of the two things she wanted most in the world.

"It can't be! It's a lie!"

"I'm telling you, the Jade Qilin is completely caught. She's bossing him around like Empress Wu, and he's just saying sorry sorry, can't even make eye contact and does everything she says, oh, it was so upsetting to watch… really…"

And her eyes were actually moist, so it seems she was really upset.

"It can't be, there's no way! What could the Peng young master possibly be lacking to serve such an ugly woman wearing a face veil!? Ha, I don't believe it."

And then she climbed the stairs hurriedly, almost running with big strides.

As soon as she reached the top, she heard the Jade Qilin's low voice, enchanting just to listen to.

What Murong Zhuji saw as she pushed through the women was-

The sight of Qing sitting next to Peng Daesan with Murong Jun perched on her lap.

"Ah, no…! Jun'er is…!"

Murong Zhuji's voice trembled.

Just how much more is that bitch planning to take from me?

On her right she had the Jade Qilin, and on her left was, um, who's that? And even her brother on her lap, three plus one extra chatting happily.

Murong Zhuji collapsed to the floor.

"Ah! Sister!"

Discovering his sister, Murong Jun jumped down and ran over.

Murong Jun, who was about to hug his sister, suddenly met Murong Zhuji's teary eyes and stood awkwardly in place.

"You, Jun'er you! How can you be with that woman!? What on earth!? Who said you could be with such a woman!"

"Well, father said she's a good sister so I should get along with her from now on…"

"What? Say that again. What did you just say?"

"Father said…"

"What! You! Why would father, you bitch."

It was the sound of Murong Zhuji's world crumbling.

Qing answered for her.

"If you're referring to Hero Murong Chengyi, I greeted him when I met him while playing with Jun'er before. It seems he viewed me favorably."

"How, how…"

Murong Zhuji muttered like that, then suddenly turned her head and shot a desperate look at Peng Daesan.

"Young Master Peng, how, how could you do this? If it were one of the other Five Flowers, yes, even that Tang clan girl over there! Then-"

"What!? I absolutely hate smooth-faced pretty boys like that too! Who are you trying to match with who? I didn't do anything!"

Tang Lan-Ah burst out angrily, leaving Murong Zhuji dumbfounded, blinking her eyes.

\textit{What's this, why is the bitch who was spewing poison about being the main wife getting angry?} she thought.

"A-anyway. Putting everything else aside, why, why are you so attached to such an ugly bitch who can't even show her face behind a veil, huh? Is it because of her breasts, her breasts? You like big-breasted women too, Young Master Peng?"

Peng Daesan let out a deep sigh.

In fact, at this rate, whether Qing revealed her face or not, either way it would just become a scandal.

Even though rumors had spread that he was involved with a beggar, even though women had loitered in front of him dressed as beggars.

No matter what kind of lover-like appearance they showed beyond this, it would just mean Qing would share some of the hatred directed at him.

"There seems to be some misunderstanding. I'm just friends with Miss Ximen, that's all. Please refrain from saying things that could harm Miss Ximen."

At this, sighs of relief filled the hall as everyone exhaled at once.

Bright whispers spread.

So they weren't in a relationship. What a relief.

Indeed, except for earlier, there wasn't any couple-like atmosphere at all. It must have just been a joke.

Of course, it wouldn't make sense for the Jade Qilin to be with such a woman in the first place.

Gaining courage, Murong Zhuji drove in the final nail.

"Is that really true? Can you really say that you have absolutely no other feelings, not even the tiniest bit?"

Peng Daesan's eyebrow twitched.

But it was a perfect question to end this scandal.

"Yes. It's pure friendship."

Peng Daesan continued after that.

"But, are you my mother? I've heard all sorts of things in my life. I'm dumbfounded. I don't know what qualifies you to ask such things."

"Ah. I just, well, I, I was just worried about Young Master Peng…"

"Worried, you say. What kind of worry?"

"Well, if rumors spread that you're associating with such a woman…"

"I don't see how it's any of your business who I associate with. And didn't I just say that Miss Ximen is my friend? Do you have a hobby of carelessly slandering other people's friends, even in front of them? Isn't gossip usually done behind people's backs? Is this your true nature?"

Murong Zhuji's face turned pale blue.

"That, that's not it. I was just…"

But how could there be any excuse?

Moisture welled up in Murong Zhuji's eyes.

Tears naturally rose from feeling wronged and resentful.

Then Murong Jun blocked in front of his sister and shouted:

"Don't bully our sister!"

Qing let out a deep sigh.

She couldn't just watch them get completely crushed, especially since she knew Jun and Jun's father.

"Stop. It's just that Young Lady Murong and I have a relationship where we exchange harsh words carelessly, so don't push it that far. Lan-Ah says this and that about you too, but it's not because she's particularly ill-mannered, right?"

"No. That one is just ill-mannered. She's become completely spoiled from being indulged too much."

"What!? You want to try me now?"

"See? You use harsh words with Lan-Ah too, right? Young Lady Murong and I just exchange harsh words too. Young Lady Murong is actually kind? Hmm? Is she kind? Well, she's not a bad person, you know?"

"You didn't sound very sure just now."

"That's why I'm saying we have this kind of relationship. Isn't that right, Young Lady Murong?"

"Th-that's right. We have a relationship where we exchange harsh words."

At this, Peng Daesan didn't hide his dubious look, but soon let out a deep sigh.

"It seems I made a mistake because I didn't know. Young Lady Murong, I apologize."

"N-no. I carelessly said something that could be misunderstood too. Ha, haha…"

Murong Zhuji laughed awkwardly.

At this, Qing opened her mouth again.

"I need to exchange some unfinished harsh words with Young Lady Murong. San, will you wait here for a moment? Young Lady Murong, I'd like to have a word with you on the seventh floor, if that's alright?"