\chapter{Dragon-Phoenix Assembly (5)}

Crack! The sharp sound of wooden swords clashing rang out, then half of one sword separated and spun through the air.

Nan-gong Shencai looked at the half-remaining wooden sword in dismay before flinging it to one side.

It was the fifth peony sword.

Qing scratched her head, feeling awkward.

"Are the wooden swords a bit weak?"

"They're carved from ebony, but hmm. This is troublesome. Sword Friend, one's sword skill doesn't improve by relying on strength."

"What can I do if I'm strong? Should we draw practice iron swords instead?"

"We use wooden swords on purpose. Isn't it because humans are weak that we use tools? Of course, in a duel to the death I would have lost immediately, but this isn't just a match to determine a winner."

Nan-gong Shencai could be called the Lu Bu of sword sparring.

In sparring using purely swords, without hand or foot techniques, no one could match him because his understanding of swords was superior.

According to the Sword King's evaluation, if he just gained some flexibility in using his hands and feet, he would immediately reach the Transcendent Realm.

Martial arts were techniques that used the body, and swordsmanship dealing only with swords was just a small part of that.

It wasn't praising his son, but a very cold evaluation as one of the Ten Great Masters under Heaven, the Sword King.

But stubbornly clinging only to the sword and struggling, he was also the main culprit for the Sword King's increasing wrinkles.

"By the way, Miss Gong's sword skill is truly sharp. Did you say it was the Xuanyuan Emperor's Sword? Indeed, it's a skill worthy of being called the Emperor's sword."

"You flatter me. I also gained many insights facing your sword. As expected, excellent sword skill befitting the reputation of the world's greatest sword clan… But was ‘sword skill' originally a word?"

"What meaning would there be in words that existed from the beginning? It's a word that swordsmen can understand, so it's sword language, the language of swordsmen."

Qing joked, giggling.

"Why, when you eat it's sword meal. When you rest it's sword rest and when you sleep it's sword sleep, why."

"Hmm? Since we don't eat swords it's not sword meal, and since swords don't sleep sword sleep seems a bit forced. Hmm. Sword rest. We could say sword rest when resting during sparring. Sword Friend, do you have any more?"

"Hmm. Chaolei married a half-sword so she's half-sword-ry. So they called her dao-ry?"

"Sword-ry! Kuk, using sword-ry now would seem like plagiarism. It's frustrating, but I must acknowledge Sister Peng's victory! And as the one who will inherit the clan, I can't abandon my duties."

"What, so you did have thoughts of marriage?"

"Actually, I don't. I'd like to dedicate my life to the sword, but as the eldest son of the Nan-gong clan, I must continue the direct line. I plan to go courting after I reach the Unrestrained Realm."

"There's one Late Stage Peak Realm and one Transcending-Peak Realm here right now?"

"Haha, the path of the sword is long and enlightenment comes quickly. Getting buried in current achievements will only lead to impatience."

It wasn't very convincing coming from someone buried in swords.

Still, it was clear that he had no burden about achievements, so it was amazing where that confidence and composure came from.

Gong Sun-Yaoyi was actually a Late Stage Peak Realm master!

Well, she had picked up a sword at five years old and swung it after every meal.

It wasn't just a figure of speech about training hard.

She really hadn't taken a single step outside the walls since picking up a sword at five years old.

Her daily routine was morning training, breakfast, training, lunch, training, dinner, training, then sleeping for two hours and repeating endlessly.

Even Qing felt suffocated just hearing about it.

"Originally, I planned to reach the Transcendent Realm and set out as a hero to raise the clan's name. But since a spot in the Ten Great Clans opened up, thanks to that I got to meet Qing, right?"

"Something, feels, something something."

Qing frowned behind her face veil.

No matter how much it was for restoring the surname or the clan's long-cherished wish, was it right to take away all of a person's time that should be most enjoyable?

If there had been even a hint of complaint about hardship in Gong Sun-Yaoyi's words, Qing would have sympathized five hundred times over, saying it was too much.

But even she herself considered it natural, having had it firmly ingrained in her mind from childhood.

\textit{Hmm, this is complete child abuse, no, Ye is all grown up now and a proper young woman, but still.}

Even Nan-gong Shencai seemed disgusted.

Nan-gong Shencai was enchanted by swords, with training itself being his job, specialty, and hobby, just enjoying it, not dedicating himself out of some duty.

He was naturally relaxed and free, a playboy who diligently wandered around playing in addition to training.

Thinking \textit{there's a real sword lunatic, I should yield to her.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Murong Zhuji's heart was broken. No, it had already been broken on the seventh floor of the Dragon-Phoenix Assembly.

"Waaah! Waaaaaaah! Waaaaaaah, waaaaaaah, waaaaaaaaah! Huk, waaaaaaah, aaaaaaah…"

This wasn't crying, but screaming out of resentment.

It was that very howl that drunk people make when they're angry at the world.

Where on earth are there people who just scream one syllable like that out of simple sadness?

At least she had her face buried in a pillow, so not much sound leaked out.

But night words are heard by mice and day words by birds, and Murong sounds are heard by Murong Jun.

Hearing his sister's crying, Murong Jun burst open the guest room door and rushed in.

"Sister! What's wrong? It's okay! Why are you crying!?"

Seeing her brother running in with a worried look when she wanted to cry, tears welled up, no, burst out!

Murong Zhuji's tears poured out.

"J-Jun'er! Hic, huuuu…"

He was once a brother who drove nails into her heart with harsh words, but knowing there was no malice, and because Murong Jun also had no chest, Murong Zhuji had forgiven him.

Of course, as a boy he naturally wouldn't have a chest, but she occasionally didn't forgive even men with chests, which was why the viciousness of the world's Sword Flower Murong Zhuji was widely spread among the rising stars.

"What's wrong! Who bullied you!? Who bullied our sister!"

"Hic, Jun'er… That bad bitch, hic, to me, sniff…!"

One of Murong Jun's advantages according to Murong Zhuji was that he was just the right size for hugging. The foolish older sister hugged her brother and sobbed loudly.

Murong Jun gently stroked his sister's back with his small hands.

"Who bullied sister? Who is it! I'll punish them. Hm? Sister, don't cry."

"Sniff, yes. Our Jun'er, as expected, sniff, I only have Jun'er. My good little brother…"

"Are you feeling better? What happened? Did someone really bully you? Tell me everything. I'll beat them up good."

Anger clouded Murong Zhuji's face again.

"Yes, that bitch, no, that woman. You know, Jun'er. Do you know what humiliation your sister suffered today? Ah, do you know what humiliation means?"

"Hmm. I don't know."

"When you're extremely sad and angry and embarrassed and feel wronged all at once, that's humiliation. And what I suffered from that woman today was exactly that humiliation. That bad bitch."

"We shouldn't use bad words…"

"It's okay to use bad words for bad bitches. And when you comfort a woman, you're supposed to take her side no matter what. So if you want to comfort sister, hurry up and repeat after me. Bad bitch, fucking bitch."

"B-bad bitch. Fucking bitch."

Surprisingly, it was faithful advice that a sister should rightfully give her brother.

When comforting a woman, you should unconditionally take her side, even if the woman is the world's worst criminal, that is the proper duty of a close man.

A man who tactlessly brings up things like 'you were at fault too' here will usually end up living as a lifelong bachelor.

However, you should stop at sympathizing, taking her side, and defending her, you must never believe what the woman says.

Because at times like this, nine out of ten things a woman says are close to fabrications, only speaking to her own advantage.

Sometimes, if there's a prefix like 'I was at fault too, but-' attached to one out of ten, you should understand 'Ah, this woman really did something to deserve a beating and came to complain to me after getting beaten', and then take her side.

"Yes, that's right, bad bitch. How could she do that to me. Jun'er, you know, today when sister went to the Dragon-Phoenix Assembly, some crazy woman suddenly started pouring out bad words at me."

"Suddenly? Without you doing anything?"

"Yes. Sister just wanted to be friendly and greeted her, but suddenly she started pouring out insults at me. And she said why is a flat-chested bitch pretending to be a woman, telling a monster that's neither man nor woman to get lost, and hitting me and pouring water… Huk, uuuu."

If Qing had been there, she would have witnessed Murong Zhuji's Righteous Karma dropping by one point.

But Murong Jun doesn't see it.

"Don't cry, okay? I'll, I'll get revenge for you."

"No. Jun'er shouldn't be involved in this."

"Why not? Sister's business is my business. Leave it to me. I'll give her a really bad, humiliation? Right? Yeah! I'll humiliate her."

"Sister is happy just hearing Jun'er say that. But it's okay. Sister needs to resolve sister's own issues. Wow, when did our Jun'er become so reliable to comfort sister like this. Hmm. Right, should we take a bath together after a long time?"

This is what it means to have a good family.

Murong Zhuji, her resentment somewhat subsided, smiled looking at her pretty brother.

"I, I'm all grown up now."

"Oh my, look who's acting all manly. Then, should you sleep with sister?"

"Uh, is that okay? I heard that's only done with married women…"

"It's okay between family. Married women are family too, so it's okay, right?"

"Yeah! Then let's sleep together!"

"How can my brother be so cute."

Murong Zhuji hugged her brother tightly.

\textit{Right, I haven't lost yet.}

\textit{It's do or die, I'll pay her back properly.}

\textit{What does it matter if I ruin my reputation a bit?}

\textit{I still have my loving family.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Peng Daesan was sitting in a place with an open wall, watching the street as the sun set.

In Peng Daesan's view, women always formed walls, so the busy street moving without paying attention to him was unfamiliar and interesting to watch.

Is this what everyone sees and lives with, he thought.

Then over there, a woman wearing a face veil.

A woman walking briskly down the center of the main street with large strides like a man.

Then suddenly her head seemed to turn this way, and she raised her hand high and waved it big, showing her delight.

Peng Daesan's mouth unconsciously stretched.

It was a smile so handsome that if women saw it, they would faint.

"Hmm, did you have fun playing?"

"Of course. Ate delicious things, ate delicious things, and. Hmm. It was delicious. Aren't you going, San? It's delicious."

"I don't know. There's no point in just chatting. The Dragon-Phoenix Assembly is just people who know each other's faces gathering anyway."

"Hmph. That's exactly what someone with no friends would say."

Qing giggled and sat down.

"Actually, I'm not sure either. Everyone's so busy buttering each other up, they don't really talk about anything interesting. And because of what Master said, I have to put on airs, so it's really uncomfortable."

"Putting on airs?"

"Isn't it putting on airs? Is that right? Disguise? Transformation?"

"It's closer to transformation. But, for saying it wasn't fun, didn't you stay quite late?"

"I just spent the whole time sparring with Sword Friend and Ye. It was fulfilling to spar after a long time. Lan-Ah left halfway through because the Tang Clan arrived and she went to see her family."

"Hmm."

"Ah. Right. I saw the Golden Sun Sword Flower? But didn't you say the Peng Clan was coming with the Murong Clan? Then hasn't the Peng Clan arrived too?"

"They arrived last night, I hear. I'm thinking of heading to the guest house soon too. I've reserved plenty of rooms here, so use them as you like."

"What, can't I go see Chaolei too?"

Then Peng Daesan shook his head.

"Come to think of it, that Tang Lan-Ah woman's words weren't so wrong. Besides, if you came representing the Divine Maiden Sect, you should receive a separate guest house. I'll come by tomorrow morning, so let's go greet the Alliance Leader together."

"Is that so?"

And then Peng Daesan stood up from his seat.

"Are you leaving already?"

"What's the point in staying? Ah. If you get hungry, I left xiaolongbao and jiaozi in the kitchen under your name, so find them and eat."

"Ooh. San! Hiya, thanks, I'll eat well."

"It's nothing. Well then, see you tomorrow."

And then he left without looking back.

Left alone, Qing leaned back in her chair and watched his retreating figure for a moment, then suddenly stood up as if remembering something and shouted.

"Waiter! Please bring out the dishes left under the name Ximen Qing!"
