\chapter{Dragon-Phoenix Assembly (1)}

In any culture, the ruling class forms their own small society.

What this small society does is incredibly simple, and if expressed in the way of Qing's homeland, it would be this:

Pulling up the ladder.

Because it's an alliance to enjoy the power they tightly hold among themselves for thousands of years.

The Dragon-Phoenix Assembly can't be free from such aspects either.

Isn't it the best networking place where young people from prestigious families build friendships and become "us" together?

So naturally, not just anyone can attend the Dragon-Phoenix Assembly.

It's not for nothing that the Ten Great Clans and Nine Great Sects know to invite and treat their disciples lavishly, it's not free, the Dragon-Phoenix Assembly participation fee is included as a considerable share.

And days like today when they hold a grand banquet are the days to repay that debt.

Even though they rented out the entire seven-story building, quite a crowd had gathered.

Of course, it's to provide ample seating since in Chinese banquet culture, people don't stand around chatting.

Because China is a standing culture, people shouldn't sit on the floor but pull up chairs to sit at tables.

"Wow, there are a lot of people."

"Hmph. Just a bunch of nobodies. There's nothing worth seeing on the first floor anyway."

"Lan-Ah. Can't you speak a bit more nicely?"

Tang Lan-Ah is not only the Blooming Poison Flower, an outstanding beauty, but also the daughter of the Tang Clan, rulers of Sichuan.

Of course, she was saying this while being the center of attention and interest as soon as they entered the building.

"Forget it. Come on, Qing'er, let's go up."

Tang Lan-Ah pulled Qing along, arm in arm.

Qing pretended to give in and gracefully climbed the stairs with elegant steps.

As they went up to the second floor, people appeared who awkwardly greeted Tang Lan-Ah.

Though no one decided it, the young people on the second and third floors were still youth from martial arts sects known in their local areas.

And from the fourth floor, youth from widely known famous sects took their seats.

It wouldn't be an exaggeration to say the real Dragon-Phoenix Assembly starts from here.

And as they climbed another floor, finally some familiar faces appeared.

"Oh, Sword Friend! Isn't it Sword Brother!"

"Young Master Nan-gong. It's been a while, hasn't it? Of course, we met yesterday, but since we only briefly greeted each other, I should say today is the day to properly meet and catch up."

"Hmm? Is it Sword Friend?"

"I have this womanly skill too, and I take it out occasionally so I don't forget. Is it awkward?"

"You. With your face covered, I'd believe it even if you said you were someone else. To think you could even pretend to be a woman properly. Hmm, is it right? You're the type of person who might send someone else to imitate you, Sword Friend."

"Do you think everything becomes a statement when Young Master Nan-gong moves his tongue? Even dogs have tongues, you know?"

"I believe you. You must be Sword Friend."

At this, Qing shook her shoulders and held out her sword.

Nan-gong Shencai bumped sword sheaths and couldn't hide his pleased smile.

"Yeah, right, is Changbin up there too?"

"Ah. Brother Changbin is on the fifth floor. Seems he went up to avoid the women."

The fifth floor is usually used by the Azure Dragon Association, and the top floor is usually used by the Phoenix Association.

Of course, it's not strictly set, so members of the Heavenly Martial Team can join regardless of gender.

But it doesn't look good for a woman to be among only men, and vice versa, so it's not easy to join unless you're particularly close or in a relationship.

Of course, it's easy for Qing.

Qing, with Tang Lan-Ah who somehow looked displeased, climbed the stairs, and peeked at the fifth floor with just her veiled head poking out.

When Qing put her index finger to her lips towards the men who saw her, they all obediently pretended not to see.

And a loud voice speaking among the crowd:

"Ha, that's why you don't have a woman. Women, you see, the female heart, you know, it's like a loach, if you try to gently grasp it, it slips right out of your hand. You have to grip it tight! Really tight to hold it in your hand, you understand?"

"Ooh, as expected of Brother Changbin. So, you're saying I should push harder with Miss Yang?"

"Of course. I'm telling you, if a man pushes, a woman will open her heart somehow. Just grab her wrist and say, Let's go! To a quiet, beautifully atmospheric place like the lakeside or garden!"

Qing approached Changbin stealthily with her index finger raised in front, taking light steps.

Everyone just pretended not to notice with mischievous smiles.

Unaware of the woman approaching from behind, Changbin continued talking, drunk on his own words.

"Just grab her shoulders and speak manly. Miss, please be my-"

"Oh my, isn't this Daoist Master Changbin? Goodness, isn't this the living legend who's mastered the female heart, said to make women fall for him with just a glance?"

"Hmm."

"Come now. Don't be like that. Since we've met like this, this girl will pour you a drink."

"Th-thank you…"

"Here. Drink it all down. Wow, how bold. Hey, Lan-Ah, what are you doing? The right side and cup of Changbin, the handsome man of Mount Hua, the slayer of women's hearts, aren't empty. Fill them both."

"Huh? Me?"

"Hurry."

"Oh, okay…"

Tang Lan-Ah hurriedly sat on Changbin's right and awkwardly poured drinks.

How much experience could the great Tang Lan-Ah have in pouring drinks?

With Qing on the left and Lan-Ah on the right, the poor Daoist Changbin with flowers in both hands stared straight ahead like a person caught between two walls.

"So, what was the latter part of that talk? Can you tell this girl that spell-like confession that melts women's hearts? I'm so curious what comes after ‘Please be my'. "

"Well…, chi-child, child, no, I mean… mother, mother."

"Mother? Your mother? Your mother wants to see me once? That's certainly a frightening phrase that melts women's hearts."

"That's not it…"

"But Daoist Master, don't you recognize this girl? Ah. How disappointing. Was I just another woman who briefly passed by for the great Changbin, slayer of women's hearts?"

When Qing spoke in a dejected voice, Changbin started sweating profusely.

Giggles spread among the crowd.

"Miss, I'm sorry… I can't remember…"

"How can you forget so cruelly when you said we'd always watch the plum blossoms of Mount Hua together? Have you really forgotten those times we spent together?"

"No… even if you say that… could you please tell me your name…"

"This girl is called Ximen Qing. Do you remember now, Daoist Master Changbin?"

"Oh! Miss Ximen? Ah, I thought your voice sounded familiar… Have, have you been well?"

"I've been fine. Ah, by the way, the young lady on your right is Tang Lan-Ah, the Blooming Poison Flower of the Sichuan Tang Clan. Lan-Ah, this is Daoist Master Changbin, Zhongyuan' top expert on women's hearts."

"This person? Women's hearts? Well, I'm Tang Lan-Ah."

When Tang Lan-Ah revealed her name, Qing counted inwardly.

One, two, "Blooming Poison Flower!" "Blooming Poison Flower!" "Blooming Poison Flower!"

\textit{That's right! Now I'm starting to understand how this works.}

In fact, this seemingly meaningless repetition of titles is imbued with respect for the other person.

"I'm, I'm Changbin…"

Changbin spoke in a volume barely audible and bowed his head stiffly like a wooden doll.

One of the Daoists sitting opposite, who had been watching while trying to hold back laughter, finally burst out laughing and asked Qing:

"Well, Brother Changbin. Did you really have a woman? How come you never introduced her to us until now? Miss, I'm Huanlu of Wudang. Since Brother Changbin is too embarrassed to speak, if it's not rude, may I ask for an introduction?"

"Ah. I'm Ximen Qing, an outer disciple of the Divine Maiden Sect. And my master is Master Ximen Surin. Hmm, yes. How is your rank?"

Then there was a sudden commotion of chairs falling and being dragged noisily.

"Huanlu of Wudang greets the elder."

"Tiansheng\footnote{田昇. Jeonseung (전승)} of Qingcheng greets the elder."

"Biwu\footnote{畢武. Pilmu (필무)} of Zhongnan greets the elder."

"Biling\footnote{畢嶺 Pilryeong (필령)} of Zhongnan greets the elder."

"Mian'e\footnote{麵惡. lit. 'wicked noodle'. Myeonak (면악)} of Kongtong greets the elder."

…

…

…

It seems the Daoist disciples who were uncomfortable dealing with women had gathered on the fifth floor.

Qing answered in a gentle voice.

"Come now, even if there's some difference in rank, I'm just a young girl who came of age this year, so there's no need to be so formal. Excessive courtesy is discourtesy, so I'm rather uncomfortable with such treatment."

"Y-yes, elder."

"Do I look that old? Elder?"

"Yes, senior."

\textit{Ah, this is the taste of being a senior.}

\textit{I wondered why those special forces veterans were so desperate not to show it.}

"Miss Ximen? You, you came of age this year?"

"Sword Friend? Coming of age?"

Nan-gong Shencai interjected in surprise.

But since Qing didn't grant permission, she just ignored him and continued teasing Changbin.

"I thought you'd gotten better, but you're still confused about honorifics? Come on, relax, we're friends regardless of rank, right friend?"

"How can I be relaxed in this setting…"

"Oh come on. Changbin, are you going to keep this up?"

"Hmm. I understand- I mean, I'll do that."

"Good. Have you been well? From what I heard earlier, you seem the same as ever. So what was it? That great confession that melts women's hearts in one go."

"Please become the mother of my child…"

"Hmm. Lan-Ah, what do you think of this confession? If you heard it?"

Qing asked for the opinion of Tang Lan-Ah, a real woman.

Tang Lan-Ah's evaluation was scathing.

"It's totally stupid. It sounds like a man with a child looking for a second wife."

It seemed quite good to me, but the local reaction was not good at all.

"Changbin, is that right?"

"Then how about ‘Please bear my child'…"

Although it was in a small voice, he had at least started talking, perhaps because they had traveled together.

It was such a surprising sight that even the Daoist members who were uncomfortable in front of elders opened their eyes wide and stared at Changbin.

"Hmm. The child part is a bit ambiguous. It's still unclear whether it's for a main wife or concubine."

"You seem particularly sensitive to that?"

"Well, anyway, if I make a marriage agreement, they'll become an adopted son-in-law. If that's not the case and I go to the in-laws' house, it absolutely has to be as the main wife."

Then Nan-gong Shencai interjected again.

"Miss Tang, since we have the opportunity to hear a woman's evaluation, I too have something in my heart. How about this confession? 'I want to share swords with you until death'. Keu, what a great line."

Then Tang Lan-Ah answered with an incredulous expression:

"What? If you share swords until death, isn't that just a duel to the death? Are you looking for an enemy?"

"Oh my, this is why they say you can't communicate with non-swordsmen."

"What? Then why did you ask?"

"I see. My mistake. I apologize. I should have asked a female swordsman. What does Sword Friend think- Ah, yes, more importantly, Sword Brother came of age this year?"

This guy, was he secretly sensitive about age?

Qing answered with a gentle smile and sweet tone.

"How about choosing your words carefully? In case you're going to say I look old."

"No, I'm not that tactless. Hmm. Well, what does age matter in sword judgment? Sword Friend, how does this confession sound to you? Until death, share swords-"

"At first I thought it wasn't bad, but after hearing Lan-Ah's words, now I can only think of it as a duel to the death. If you fight until one of you dies, it's a duel to the death, right?"

"Indeed, after hearing it, I did have an ‘oops' moment. Then hmm, yes, for a lifetime, I want to share swords for a lifetime. Oh. This is also a great line. Miss Tang, how about this time? It's my best confession."

"It's better than a duel to the death. But does it have to be sharing swords? Is a sword some kind of Hebi? To share swords?"

Hebi\footnote{合璧, jade annulus} was something that was once popular, where a single ornament was divided into pieces and kept by each other.

It was used between lovers, and also often used by men who secretly kept mistresses and two households to give to their illegitimate children.

Then Sword Friend added more.

"Oh. That's a good idea too. If we divide the sword and use it as a token of promise… hmm, that won't work, if we divide the sword it becomes a half-sword, doesn't it?"

"Indeed, a half-sword is a major issue. Besides, if you split a sword, you can never win."

Qing nodded in agreement.

They say the fifth floor is done and the sixth floor is a resting place.

The seventh floor is where the women who are tired of men's nodding, the Phoenix Association members, gather.

\textit{Since we've come this far, I might as well take a look around.}

\textit{And honestly, I'm curious about what clothes the Blooming White Lily is wearing.}

\textit{When I saw her briefly yesterday, that outfit was so desirable and good to look at.}

\textit{Yesterday I couldn't look closely because I had business with Gong Sun-Yaoyi.}

\textit{Hmm, she's probably wearing a deeply cut outfit again today?}

Qing climbed the stairs with an excited, pounding heart.