\chapter{Dragon-Phoenix Assembly (7)}

Even before Qing entered the Dragon-Phoenix Assembly banquet hall, there was a woman lingering at the entrance.

As soon as she saw Qing, her expressionless face subtly came to life and a smile blossomed.

Gong Sun-Yaoyi approached Qing quickly with a brisk walk that wasn't quite running.

"Miss Ximen, hello again today? The weather is so nice, isn't it? On a cool day like today, cool… On a day like today what do normal people do I only know training so I'm sorry I'm sorry for this…"

"Yi, calm down. What's this, why are you like this again? I'm glad to see you too. You don't need to put so much effort into greetings, so don't feel burdened."

"Ah. That. Um, there's someone I'd like to introduce, if it's alright I'd like to humbly ask if it would be okay to do so and I hope you'll graciously allow it…"

\textit{What's this? Asking if it's okay to ask?}

\textit{Why, isn't it possible to infinitely repeat asking if it's okay to ask if it's okay to ask?}

As Qing tilted her head, Gong Sun-Yaoyi noticeably fidgeted, watching Qing's reaction.

"Who is it?"

"It's my foolish little brother…"

"What, you had a brother too? Where is he?"

"Well, Tianri."

"Yes, Sister."

Then, as if he had been waiting, a young man walked out with small steps.

Somehow their features were remarkably similar, to the point where the siblings looked almost identical.

Since Gong Sun-Yaoyi was pretty even with a plain face without makeup, her similar-looking brother was also a handsome young master who could easily set women's hearts aflame.

"I am Gong Sun-Tianri\footnote{公孫天日. Gong Soncheonil (공손천일)}. I've heard a lot about you from my sister. So you really exist. I'm truly grateful that you've become friends with such a shut-in."

Gong Sun-Tianri's greeting was like that of an actor in a play, with large, showy movements and precision.

Even insignificant movements were made with big lines, making for an impressive etiquette that was nice to look at.

"I-I told you she was real."

"Hmph. It's almost at the level of a coincidence like falling off a cliff and finding a secret martial arts manual piled up inside a cave. In the end, sister didn't do anything, and she just became friends with you. You're practically her lifelong benefactor, aren't you?"

"Ugh. I-I know."

Qing tilted her head.

\textit{What's this? Something something.}

"Oh my, excuse me. My sister is lacking in worldly experience, but please guide and teach her."

As he said this, he gently smiled at her, and while a handsome guy smiling is nice to look at, what's this, doesn't it feel like he's flirting?

Qing was unsure and reserved judgment for now.

"Young Master Gong!"

"Ah, Miss Yeon. Have you made up with your friend?"

"Thanks to you! Um, so, if you have time, maybe even just a meal…"

"Oh, I'm sorry."

"Ah…"

"I should have invited you first. My lack of perception made you say such difficult words. Will you please forgive me?"

"Oh. Y-yes, then, n-next time…"

The woman called Miss Yeon, with a bright red face, fled without even making plans.

And after that, similarly, Miss Cheon and Miss Yun exited, and Miss Sanying ran towards Gong Sun-Tianri but saw Qing and hiccupped, quickly retreating.

\textit{This guy. His skill at leading people on is not ordinary.}

"Ah, Sword Friend!"

"Oh. Sword Friend has come. Miss Gong is here too. Well, shall we have another enjoyable sparring match today?"

"A bit later. I haven't eaten yet. Right. This is Gong Sun-Tianri, Miss Gong's brother. This is Sword Friend, or Sword Lunatic. Nan-gong Shencai."

"The Young Sword King Nan-gong Shencai of the Nan-gong Clan!"

\textit{Isn't his exclamation a bit long?}

"Haha, I've decided to change my title from Young Sword King to Passionate Swordsman now. I'd be grateful if you called me Passionate Swordsman instead of Young Sword King."

If the Sword King heard this, he'd say this bastard who doesn't listen to words now even threw away his father's title because he doesn't want to inherit it, and add another bottle of liquor.

The Sword King, whose drinking increases day by day, I wonder if his liver health is alright.

"Passionate Swordsman! Just hearing it makes my blood boil. Is there a story behind it?"

"The Sword Friend next to you gave it to me, moved by my burning passion for swords. It had an emotion I'd never heard before, so I decided to make it my lifelong title."

"Aren't titles usually given by others…"

"Didn't Sword Friend give it to me? You're also an elder at the level of a sect leader, so you're more than qualified."

"But hearing about sparring…"

"What, is your blood boiling? Then right away."

"No. I'm hungry. I woke up late and just ate a few rice balls."

Rice balls refer to steamed glutinous rice wrapped in bamboo leaves.

Strangely, they were characterized by being made in a triangular pyramid shape.

There were various fillings, some salty with meat, others sweet with red bean paste.

"A few? Exactly how many?"

"The ones with lamb, goat meat, chicken, and duck egg were delicious. And the red bean was a bit, being sweet it didn't feel like a meal."

"You ate five from the morning and you're still hungry?"

"No, six. I ate two of the duck egg ones because they stuck to my mouth."

Then Nan-gong Shencai's expression darkened.

And then, he asked in a voice full of concern.

"Are you alright? If you're still hungry after eating that much, there must be something wrong with your body. It would be best to get examined by a physician right away."

Two rice balls are equivalent to one heaping bowl of rice.

Eating six of those and saying you're still hungry was such a strange thing that even pigs would be ashamed and reduce their appetite.

"Lan-Ah always checks on me? She says I'm healthy. But she doesn't know why I eat so much."

"Miss Ximen, don't worry. Generally, a big appetite corresponds to three of the five blessings of the body, so isn't it truly fortunate?"

"Ah. Thank you for saying that. Somehow everyone's been scolding me more and more for eating too much…"

Finally, they settled at a table and just as Qing was about to sit down.

"Miss. Excuse me for a moment. Here."

And then Gong Sun-Tianri spread a handkerchief on Qing's chair.

"Young Master Gong? Are you usually this kind to women? You should be careful as it could easily be misunderstood."

"Misunderstanding, you say? Miss, is it really a misunderstanding?"

And then he smiled gently again, and Qing was certain.

\textit{Ah. This wasn't uncertain at all.}

\textit{He's totally hitting on me right now.}

\textit{This is why I go around with my face covered.}

\textit{Oh, but my face is covered?}

Even Gong Sun-Yaoyi hasn't seen Qing's bare face yet.

Isn't it common sense in Jianghu that women who cover their faces all have their reasons?

Gong Sun-Yaoyi, who forgets how to breathe or uses extreme honorifics just to make one request, would probably never be able to ask to see her face in the future.

But do friends not know each other's faces?

She was thinking of inviting her to the Wucheon Pavilion today since she was bored and showing her face too.

"Young Master Gong. That won't do. You shouldn't tease a woman whose face you haven't even seen like that."

"What use is beauty or ugliness? My sister praised you all last night until late, so isn't it not strange to harbor feelings of admiration for your character?"

At this, Qing's head turned towards Gong Sun-Yaoyi.

Gong Sun-Yaoyi lowered her head deeply, but her exposed ears were completely red, so there was no need to confirm the truth.

"I appreciate your feelings, but I have personal circumstances that make me uninterested in matters between men and women, so please find another good woman."

"Is that so. But a person's heart doesn't leave just because you say to put it away. I'll just keep it in my heart, so please don't feel burdened. Just remember me someday if your heart changes."

\textit{Ugh.}

Qing made a disgusted expression.

It was an advantage of the face veil.

They don't know what expression you're making anyway.

So when she finished eating and said she was going to the seventh floor, Gong Sun-Yaoyi couldn't hide her apologetic look.

"Miss Ximen, I'm, I'm sorry. I was meddlesome. I said you were like an older sister and I wanted to be family like a real older sister, and my brother said if that was my wish then- I really didn't know he would act like this, so please don't be upset or offended and with your broad-"

"Calm down. Well, your brother is kind in a way. Trying to make his sister's friend family by seducing a woman whose face he doesn't even know, oh. Is this kind? Should I say it's bad?"

Qing was confused.

Suddenly coming up to the seventh floor to avoid her friend's brother who was coming on to her, somehow the chatter seemed to die down a bit.

Qing, who didn't care anyway, scanned the crowd with shining eyes.

\textit{Lily, where's Lily!}

\textit{Where is Teacher Chen Sui, the pioneer of radical clothing?}

Chen Sui was also one of the Five Flowers of Wulin with extraordinary beauty, so she could be easily found just by her face being dazzling even without her outfit, but unfortunately it seemed Lily hadn't come.

Still, her eyes were dazzled twice, once because Murong Zhuji was over there, and on the opposite side was another beauty she was seeing for the first time.

Since there was always someone around Qing to explain things, a question similar to talking to herself naturally popped out.

"Hmm? Who is that?"

"I wonder too. Who could it be?"

However, Gong Sun-Yaoyi was a complete newcomer who knew even less about Wulin than Qing, not just Wulin but she barely knew Jianghu at all.

With two fools together, even with four eyes they knew nothing.

That's when it happened.

"Oh my, Miss Ximen!"

Someone pretended to be glad to see her, so she turned around and what do you know. Murong Zhuji was approaching Qing with a bright smile.

\textit{What's this? There's no way she'd be glad to see me? Was she such a great hero?}

\textit{Perhaps she was a miss with no breasts but a heart as big as breasts?}

"I was too rude yesterday. Thinking about it, it was all my fault, so I was determined to apologize if I met you again."

"It's okay. We agreed to forget about it, didn't we?"

"Does that make what happened disappear? As fellow female martial artists, I was hoping we could have a place to clear the air in a martial artist way."

\textit{What's this, is she asking for a fight?}

\textit{Does she think she can win if we fight with swords?}

As Qing was thinking this, Murong Zhuji continued.

"Do you like alcohol by any chance? From ancient times, heroes have dissolved all their frustrations and resentments in wine cups and let them flow away, isn't that the way of martial artists? Please, don't refuse and let's drink together and get to know each other pleasantly? Okay?"

"Alcohol. I like alcohol."

Qing answered.

It was an answer that sprang out quickly from her spine, not her brain.

Murong Zhuji's name uses the characters for 'pearl' 珠 and 'noble woman' 姬.

However, the 姬 for 'noble woman' is not just for women but an honorific character attached to high-status women.

Right away, the Divine Maiden Sect enshrines the Wu Mountain Divine Maiden, and this Wu Mountain Divine Maiden's name would be Yaoji.

In the past, the emperor's daughter was called Wangji and the old word for princess was Jehi, so 姬 was a more elegant and beautiful character than 女 for 'woman'.

However, her close friends say it would be more accurate to use the character for 'alcohol' 酒 instead of 'pearl' 珠.

This is because Murong Zhuji is a heavy drinker.

Often, a heavy drinker means someone who downs alcohol by the mal.

One mal is roughly equivalent to about 18 liters (610 fl.oz) in Qing's homeland, an ultra-large volume that would be thirty and a half grande-sized cups of the traditional Korean drink iced Americano brewed from roasted beans.

So a heavy drinker means someone who drinks that much alcohol.

The Chinese have believed since ancient times that liver detoxification ability is proportional to one's character.

Of course, limited to men.

If a woman is a heavy drinker, they criticize her saying she'll make mistakes while drunk, so a woman's liver doesn't have much use.

This is also why the monsters in folktales covet only men's livers, leaving women alone.

However, Murong Zhuji was not a female activist who would rise up indignantly against this, shouting about the filthy ideology of male superiority and trying to overturn the rotten world. (There are separate activists)

\textit{Women only make mistakes when they drink?}

\textit{Then doesn't that mean if you make them drink, they'll make proper mistakes?} she thought.
