\chapter{Dragon-Phoenix Assembly (9)}

Meanwhile, Qing stood up alone, dusting off her robe and said:

"Oh my, Miss Murong? Are you perhaps drunk? Why are you suddenly rolling on the floor? I was so startled I jumped up. Ah, was this perhaps your creative method of trying to help me up?"

"Th-the floor is a bit slippery. Miss Ximen is surprisingly! Quite! Heavy it seems. I lost my balance pulling such a heavy weight, like some iron lump! Heavy! Thing, Miss Ximen didn't look like it but her weight!!! Oops, sorry. I misspoke. There was absolutely no malice intended."

Yesterday Qing had rapid-fired only at weaknesses, so Murong Zhuji was dumbstruck, but Murong Zhuji's vicious tongue doesn't lose anywhere else.

Qing thought.

\textit{Only women care about weight. Does she think I care about such things?}

\textit{It doesn't hit at all and doesn't even make me feel bad?}

\textit{You should know your opponent before attacking, you, you stupid, empty-headed, damned bitch.}

\textit{I really, truly, not even a tiny fraction of a bit feel upset, okay?}

\textit{Who gets scratched by such childish words?}

Qing, who wasn't hit at all, answered:

"No. It's the truth, so what is there to be sorry about? Because I have heavy lumps of flesh hanging on my chest. I really envy Miss Murong. Your shoulders must be really, really, very, very light."

Qing's superhuman hearing didn't miss the sound of Murong Zhuji grinding her teeth.

"Oh! No! That's not it! Are you alright!? I have something to cushion me when I fall. Don't you not have that, Miss Murong? It must hurt more than me, I'm so sorry, because it's heavy, aish these wretched breasts, if I could give them away I'd like to share them."

As Qing slapped her chest repeatedly, blaming it, veins popped out clearly on Murong Zhuji's forehead.

"I-I don't need them, ugh. Alright, today, let's drink ourselves to death. Let's see. Let's settle this once and for all."

Murong Zhuji's voice trembled.

As she tried hard to think.

\textit{Endure. Endure.}

\textit{Anyway, before the drinking contest I'm drinking tea and that bitch is stupidly downing alcohol without knowing, so.}

After returning to her seat and emptying about two bottles, the woman who went down earlier came back with news that preparations for the drinking contest were complete.

Qing tilted her head.

There's nothing here, what preparations are done?

Then Murong Zhuji said with a proud, evil expression, showing off:

"Now, shall we go for the real contest?"

In Zhongyuan, drinking capacity was a very important issue directly linked to a man's pride.

An example of this would be Zhang Fei.

What happened to Zhang Fei after he drank and caused trouble while drunk?

While sleeping drunk, when a blade touched his neck, thinking it was a mosquito landing, he struck the back of the blade hard with his hand, cutting off his own neck in one stroke.

In other words, it wasn't assassination but suicide.

How dumbfounded must the two assassins who came to behead him at the risk of their lives have been?

It could be said that the two older brothers who didn't correct their younger brother's behavior early on killed Zhang Fei.

Despite drinking so much usually, how did his brothers act?

They acted like overprotective parents, saying a hero should be able to drink and cause some trouble when drunk, why are you killing our brother's spirit?

Because drinking capacity is a man's pride, and a younger brother's pride is the sworn brothers' pride.

Thanks to this, he completely evolved into a bastard, whipping all subordinates he saw whenever he drank.

Only then did Liu Bei pretend to stop him-

Saying he should refrain a bit because he might get backstabbed if he acts like a dog, but even that was out of concern for Zhang Fei.

The lowly subordinates who were whipped to near death by his sworn brother could just be replaced if they died, but the one remaining brother couldn't be replaced.

To Liu Bei, even a son was a trivial existence that could be replaced by having another (though he wasn't the one giving birth), so what did nameless soldiers matter?

We must not forget that Liu Bei was the worst ruler who threw away all his ministers and people like trash after losing both his brothers.

Anyway, when Zhang Fei drank, his sworn brothers applauded and praised saying our brother is the strongest, sending him out to every banquet to establish discipline with his drinking capacity, not distinguishing between friend and foe.

This is what drinking capacity means to Zhongyuan men.

In fact, this was the same not just for Zhongyuan but for the whole world.

So drinking capacity could be said to be some instinct touching on the essence of men, transcending cultures.

So in Zhongyuan, when it comes to drinking contests, there's a somewhat established system.

The rules of drinking contests were as follows:

Place a barrel of alcohol on the table, and next to it float a gourd dipper in a vat of alcohol.

You can only put your mouth to the barrel once, after that you have to pour the remaining alcohol over your head.

Since you lose if your upper garment gets soaked, it was important to empty it cleanly without spilling when you put your mouth to it once.

There were several other conditions for defeat.

Withdrawing saying you can't drink anymore is a loss.

Breaking the alcohol barrel because you can't control your body is a loss.

Vomiting is a loss.

If you get caught pushing away drunken behavior as a bet, you're the world's biggest bastard.

If the alcohol runs out, whoever goes to urinate first while waiting is considered the loser.

Of course, going to the toilet before the alcohol runs out is an immediate disqualification loss.

This was the true trap Murong Zhuji had prepared, and the friend (lackey) she sent to prepare went around each floor enthusiastically spreading word of the drinking contest between Golden Sun Sword Flower and the Veiled Woman.

For reference, the choice of words 'Golden Sun Sword Flower vs Veiled Woman' was truly malicious, a mysterious move to frame it as a contest between one of the Five Flowers of Wulin's top beauties and an ugly woman hiding her face.

Thus, a dueling arena was created on the first floor.

The Heavenly Martial Team and Earthly Dragon Team of the Dragon-Phoenix Assembly, and even the rising stars of small and medium sects not yet affiliated with them gathered, so all the dining tables and chairs had to be cleared away.

Of course. It was a formal drinking contest between women that would be hard to see in a lifetime.

In a world where it's not even easy to hear women boasting about their drinking capacity, they were going to have a public contest in front of people.

And so Qing and Murong Zhuji faced each other across the table with the alcohol barrel on it.

And in between, Qing tilted her head.

\textit{But who is this person acting as referee in the middle?}

The answer was the owner of the tower.

However, not just Qing but everyone was uninterested so no one knew.

"Now, one cup!"

The tower owner said this and started scooping alcohol from the vat into the barrel with a large dipper.

A dou (斗) is a ladle for scooping alcohol, and the Big Dipper (北斗) constellation uses the same character, meaning seven stars shaped like a ladle in the north.

Murong Zhuji was confident.

She had already somewhat solidified the victory on the seventh floor, rather it was hard work drinking tea earnestly.

Compared to that, that bitch had just emptied seven bottles of that strong Dugang wine.

Qing just admired it a bit.

So this was the plan built up for this.

Not to catch weaknesses while drunk and tease, but to properly show shameful behavior in front of everyone.

However, she picked the wrong opponent.

Sun Tzu, who shouted 'Know yourself and know your enemy', was continuing to build his undefeated myth of continuous victories and hundred battles hundred wins today.

Just as Qing was about to lift the barrel:

"Wait! Miss Ximen. Shouldn't you take off your face veil? Isn't it too unfair for me like this? Even if you leave some on your head, if the face veil absorbs it, it seems that much more unfavorable for me. The more precious the silk, the more alcohol it will absorb."

Silk refers to the silk woven face veil.

These were the words of a woman who had been drinking tea while making Qing drink alcohol.

Then the crowd's gaze focused on Qing.

The sound of someone shouting "That's right!"

Qing laughed and retorted:

"Shouldn't Miss Murong endure this much? Even if Miss Murong spills while drinking, your upper garment won't get wet, right?"

Qing said this while making a hand gesture as if stroking a beard.

In fact, it was expressing water droplets falling from the chin, so people immediately understood the true meaning.

The crowd's gaze busily went back and forth between Qing's chest and Murong Zhuji's chest.

Someone shouted "That's right!" again, causing an uproar of laughter in the crowd.

Murong Zhuji's tightly clenched fist trembled.

And so one barrel.

"Two cups!"

And two barrels.

"Three cups!"

"Four cups!"

"Five cups!"

By this point, some spectators started to look pale.

Murong Zhuji staggered slightly as she put down the barrel, barely taking a step back to regain her balance.

"Oh my, Miss Murong? Aren't you overdoing it? I'm just starting to feel a bit tipsy, how could such a delicate person challenge me to a drinking contest?"

"Who's, drunk. I'm not drunk! Next cup!"

The spectators thought: She's drunk. She's drunk.

"Six cups!"

"Seven cups!"

By this point, the outcome was starting to show.

Murong Zhuji's narrow-sleeved red jacket was half soaked and clinging to her body.

Meanwhile, Qing's martial attire was clean without a trace of moisture.

"Miss Murong. Wouldn't it be better to recognize your shortcoming and withdraw at this point? I'm worried you might show an unsightly appearance in front of all these people…"

"Shut up! Who's, drunk…"

"I didn't say you were drunk. You seem very drunk though…"

"Next cup! Bring the next cup!"

"Eight cups!"

The tower owner said this and started scooping alcohol.

Qing let out a deep sigh.

\textit{Although her intention to humiliate me in front of all these people was truly despicable, wouldn't this lead to a big incident?}

\textit{If she had accumulated Evil Karma, I'd finish her off right now. But she hasn't, so it's not something an adult should do to humiliate an innocent woman.}

Qing lifted the barrel to drink, then suddenly let go, causing a loud crashing sound as it shattered.

"Oh my. It seems I've lost. Miss Murong has won the drinking contest, so I'll withdraw now."

Qing said this, but none of the spectators thought so.

Anyone could see it was a gesture of losing on purpose out of concern for the opponent, so whispers spread here and there saying the veiled woman seems to have a truly kind heart.

\textit{Ugh. I'm so full I could die.}

Qing forcibly suppressed the urge to rub her stomach as she headed for the stairs.

Even if withdrawing, shouldn't she take care of the collapsed Gong Sun-Yaoyi?

Thinking she should ask for some hangover soup to be made at the Wucheon Pavilion, she was pondering whether clear or spicy would be better.

"Hey! You! Stop right there! What are you doing!"

"Isn't it the law that the loser withdraws silently? It's hard to control my body today so I'm going back, please show magnanimity as the winner."

"You, you! Are you mocking me!? You're putting on airs just because your breasts are a bit bigger! Fine, I'm a flat-chested bitch! I have no breasts, but what have you added to me!?"

It was a grand self-destruction.

\textit{Oh dear, I withdrew to avoid seeing this.}

Qing let out a deep sigh.

"Miss, you're very drunk."

"Yes, this is all fake too! So what! You bad bitch! Poking at people's sore spots. Tsk, what's the use of this stuff!"

And then she stuck her hand into her chest and pulled out a sewn bundle of cotton padding, throwing it away.

And then she let out angry breaths, when suddenly tears started streaming down.

"Tsk. I too, like this, tsk…"

Moreover, because she only pulled out the fake breast on one side, one side was modestly rounded while the other side collapsed like a man's.

If she had pulled out both sides it might have been okay, but the contrast made her look even flatter.

Qing, unable to bear the sight, spoke again:

"Could Miss Murong's friends please…"

Then her group, who didn't know what to do, swarmed around Murong Zhuji.

"What! Let go! I said let go!"

"Zhuji, stop it. We all understand how you feel, we're all upset too, so let's not do this and first go upstairs…"

"How would you know! You all have at least a little! No one knows how I feel! They don't know! And it's not just my breasts that are small! I have something big too- mmph!"

One of her friends who couldn't bear to listen anymore firmly covered Murong Zhuji's mouth.

With both arms firmly restrained and her mouth covered from behind, Murong Zhuji was completely subdued and dragged away.

And then a solemn silence descended on the hall.

Thanks to this, only the muffled sounds of her still screaming stood out.