\chapter{Dragon-Phoenix Assembly (3)}

A beauty appeared out of nowhere and immediately spewed harsh words.

It was truly a premonition of trouble.

Qing decided to observe for now.

At the moment, the newly appeared woman just seemed like a bad person one-sidedly, but there might be a story between the two that Qing didn't know about.

Perhaps they were from enemy clans, or had some unresolved grudge from the past making them adversaries.

Or Qing might be misunderstanding by seeing only a part, and they could be such close friends that they exchange insults instead of greetings.

You know, some men get excited and build deeper friendships by insulting each other as soon as they see each other's faces.

Not just men, but women too could build deeper friendships by exchanging coarse insults like 'you bitch' and 'you whore.'

And above all, it seemed like it would be interesting.

The situation was getting more and more intriguing.

As the woman who appeared with personal attacks walked forward boldly, women sitting at three tables on one side greeted her warmly.

They were clearly the woman's group.

Qing looked around and pulled a plate of fried snacks called sachima in front of her.

It would be nice to have popcorn popped like snow, but since it doesn't exist in Zhongyuan yet, she'd have to watch while eating something else instead.

"That Sword Flower bitch…!"

The sound of Chen Sui grinding her teeth next to her.

Then it suddenly occurred to her, isn't Golden Sun Sword Flower Murong Zhuji the older sister of that Murong kid?

Qing unconsciously looked at the woman's chest, then tilted her head.

\textit{Hmm? It's not that there's nothing?}

\textit{Though modest and simple, there's clearly a proper shape, so it's not to the extent of saying there's nothing at all.}

As Qing was thinking this, Chen Sui delivered her lines in an angry tone.

"What are you trying to do now?"

"Oh, what! Lily! Are you angry? Oh my. I already said I was sorry. People can make mistakes, and besides, only vulgar women in brothels wear such clothes that expose their bodies. I made a mistake because I was confused. I'm really sorry."

Her skill at apologizing while insulting was extraordinary.

In this situation, getting angry would only make one look narrow-minded, so it was actually a technique to provoke anger.

Chen Sui, her earlobes turning red, tried hard to steady her voice as she responded.

"Yes, people can make mistakes. But it's a bit perplexing that you're picking on perfectly normal clothing."

"Normal? Ah! Right. Come to think of it, it wasn't a problem with the clothes. I saw courtesans passing by earlier with everything exposed down to their solar plexus, showing off their small breasts, so I must have been confused. Ah, I'm really sorry for the confusion. But anyone would, no, no."

\textit{Wow, she's good at turning it around.}

Qing munched on snacks vigorously with an excited heart.

So far, Miss Jin is in a one-sided losing situation! Can Miss Jin turn this disadvantage around?

That's when it happened.

"But who's that person next to you that I haven't seen before…"

Suddenly Murong Zhuji turned her gaze to Qing.

Although it's through a face veil, Qing's veil is a top-of-the-line, ultra-premium product that allows her to see outside freely.

As Qing looked back, their eyes didn't meet because Murong Zhuji's focus was a bit lower than that.

"Oh my, who is this? Did all the energy that should go to her head get stuck in her middle dantian? Or ah, it seems she's hiding something inside, ah, looking at that poor sight, miss over there, you shouldn't secretly hide food from the banquet in your bosom like that? But, who are you?"

Qing's mouth split into a wide grin.

\textit{What's this, look at that. Why suddenly at me?}

Of course, there was a presence there that couldn't be hidden even by martial attire, because it was a huge evil that Murong Zhuji had never seen before.

But Qing didn't know that circumstance.

The middle dantian stuff isn't a problem.

Qing was already sufficiently endowed in that area, so she had the magnanimity to just pass over such unsightly jealousy with pity.

But to say it's a poor sight?

Qing was wearing Divine Maiden Sect robes.

"Oh my. What did you just say?"

"Ah, I'm sorry. I didn't mean to offend you, I was just trying to give some advice. If you're coming to the Dragon-Phoenix Assembly, you should dress properly. What kind of appearance is that? Who on earth invited such a beggar- ah, sorry. Such a woman? Lily, was it you again?"

"How can someone be so rude…!"

As Gong Sun-Yaoyi was about to stand up abruptly, Qing stretched out her hand to stop her.

At the same time, she grabbed Tang Lan-Ah's wrist and said:

"I'm fine. Ye shouldn't damage her reputation any more here. And Lan-Ah, put that poison bottle back."

"But that crazy bitch…"

"Forget it."

Qing smiled coldly.

"Miss? I'm sorry, but could you speak up a bit? I can't hear you."

"Oh my, is there fat in your ear holes as well as your middle dantian? Can't you hear me?"

"It's not that, since sound originally comes from the chest, when someone without a chest speaks, I really can't hear at all. You keep opening and closing your mouth so it seems like you're saying something, but Miss Chen, can you hear her?"

Chen Sui snapped back to her senses.

"No? I was just thinking how quiet it was."

"That's right, isn't it? Are you perhaps sleepy, miss over there? Why do you keep yawning over and over?"

"Haa? Do you know who you're picking a fight with-"

"Ah. Right. I was just having an interesting conversation with Miss Chen, would you all like to listen too? I heard there's a Zhongyuan's largest market in Kaifeng, so I went to take a look."

Qing continued, speaking playfully.

"And you know what they were selling? Small pouches filled with cotton. When I asked what they were for, oh my goodness, wow, don't be surprised. They say women without breasts use them to stuff inside their coverings to deceive people. Miss Chen, can you believe this?"

"Oh my my my! Is that really true!? I can't believe it. It's unbelievable."

"Right? I was so surprised that such a useless item exists. Where on earth are there women without breasts? No, if a woman has no breasts, isn't she just the same as a eunuch with his manhood cut off? Don't you think?"

Suddenly, killing intent rained down.

Not just Murong Zhuji alone, but all the women gathered around her, the entire group, had their eyes filled with venom.

\textit{Ah, that faction is generally a bit low in altitude.}

"You bitch, just because you have a hole for a mouth…"

"Oh my, why are you yawning with an angry expression? By the way, Miss Chen, who is that scary eunuch official glaring at me? Could you introduce me?"

Chen Sui hesitated for a moment.

She should play along well, but should she say she doesn't know or pretend not to know and introduce her?

But there was no time to hesitate, so Chen Sui made a choice, thinking 'whatever'.

"Ah, that's not a eunuch but Miss Murong Zhuji of the Murong Clan."

"Golden Sun Sword Flower! Ah, that famous Sword Flower of the Five Flowers of Wulin. No wonder, I thought she had a body very advantageous for swordsmanship."

"What do you mean a body advantageous for swordsmanship?"

"With such a light and thin body, you can definitely extend your sword smoothly without anything getting in the way. Look at me, when I do this, this, my breasts get in the way. Oh my, being born like this is really disadvantageous as a swordsman."

"Ah. Your distress must be great."

"So when I see someone with such a body advantageous for swordsmanship, as a fellow swordsman, I'm not really envious. Hmm. Yes. Even if it's uncomfortable, a woman should still have ample bosom, after all."

Qing fired off words rapidly.

It was a vicious tongue that even Zhuge Lixian, the top intellectual among muscle men, failed to hold back exclamations of admiration for.

Murong Zhuji's face turned bright red.

"Hey! You! Are you done talking!?"

"If you want to speak to me, could you at least look at me while speaking? Why are you talking with your back turned?"

"Huh? What? You can't even see in front of you? Who's turning their back?"

"Ah, are you facing forward now? It's so flat and without curves that I thought you were showing your back. But, doesn't anyone think that looks like a back view? How can a woman have such a flat figure like a man, oh my! I see!"

Qing then bowed her head.

"I'm really sorry. I didn't know you were in women's clothing. You must have your reasons for pretending to be a woman. I'm a bit lacking in perception. So you're a eunuch hiding your identity, right? I understand. Should I call you miss too?"

"Who, who's in women's clothing!"

"Alright. You're not in women's clothing. Okay? I absolutely haven't noticed anything, so you can rest assured. I'm a woman with a mouth as heavy as those breasts. Only someone with a light body and heart from having no breasts can speak so lightly, mocking and calling others courtesans and such vulgar things."

Chen Sui cooled her burning insides with tea.

\textit{Wow, what's with this woman? What kind of tongue is that?}

\textit{If I had picked a fight and made her an enemy, I would have been completely destroyed, she thought.}

\textit{The beaten Sword Flower seemed pitiful.}

\textit{Actually, she wasn't pitiful.}

Oh my, it's like drinking iced fruit tea in midsummer, she thought, struggling to suppress the corners of her mouth that were twitching upwards.

"Y-you, you…"

"Hmm. Since you've gone to the trouble of dressing as a woman, how about this? If you take a beehive and stick it to your chest as a cover, wouldn't the bee stings make it swell up a bit? Or, ah. If bees are too much trouble, how about slapping your palms vigorously? Bruises make the flesh swell, right? The color won't show if you cover it anyway."

"Eek…!"

"Ah! Fake breasts! That's what those items the merchant was selling are for! They're not for women to use, but for people who need to become women! They say everything in the world exists for a reason, indeed it wasn't a carelessly made item."

Murong Zhuji just panted, unable to answer.

Tears were welling up in her eyes.

"Please don't take my words lightly. They say when Nüwa molded humans, there was no gender distinction so men and women were the same, so later to differentiate, she attached manhood to men and breasts to women. So if you're trying to imitate a woman, the size of the breasts is a very important matter…"

"Hey! Shut your mouth! Just because you have a hole for a mouth!"

"Oh my, are you saying the mouth should be blocked rather than open? Just as it's natural for a woman's breasts to be protruding, shouldn't the mouth naturally be open too?"

"This bitch keeps talking about breasts, breasts, who wanted to be born like this, this is why I hate big-breasted bitches!"

"Hmm. It's not your fault that your breasts are small, or rather non-existent. But isn't it your fault to be jealous and bite at others because you don't have any? Did you know who I was when you insulted my robes?"

"Hmph, it's just some shabby robes anyway."

"My name is Ximen Qing, and these are robes personally made by Master Ximen Surin, the Zenith Among Women, for her named disciples. Are there any Daoist children in your Murong group? What's your rank? Won't you greet an elder even when you see one?"

At Qing's words, chairs fell over with a loud crash.

"Sanhe of Qingcheng greets the elder!"

"Sanying of Qingcheng greets the elder!"

"Wulin of Mount Mo pays respects!"

"Mayuran of Chengwol Sect greets the elder!"

"Changyang of Mount Heng pays respects!"

"Right. How can Daoist children be hanging around such a harsh child? How heartbroken the elders of your sects would be if they knew."

"Ah, no, that's not it!"

"Yes, don't stay in such an embarrassing place, go somewhere else. I'm not good at remembering faces, so if I don't see you, I'll forget about it right away."

"Yes! Thank you!"

The five of them quickly vacated their seats, hiding their faces and fleeing downstairs.

And then Qing stood askew with her arms crossed, as if to say 'What are you going to do now?'

For reference, Qing has no history of crossing her arms since entering Jianghu. It's because it's uncomfortable.

But by deliberately crossing her arms, pressing them tightly from below her solar plexus and lifting up, her imposing presence was like that of a steep mountain, the spirit of Mount Tai.