\chapter{Dragon-Phoenix Assembly (12)}

Drawing a straight line from heaven to earth.

Pressure of Mount Tai. Heavy as if Mount Tai is pressing down.

Swinging in the shape of the earth, drawing a straight line.

Thousand Army Lateral Sweep. As if cutting down a thousand soldiers.

Thrusting straight in the shape of a point.

One Person Will. Penetrating everything with one.

Even if grandly packaged, in the end it was nothing more than downward cutting, horizontal cutting, and thrusting.

Nevertheless, Qing's movements were so powerful that the terrifying sound of wind being cut rang out shwaek shwaek.

Rather than any particular enlightenment, it was simply because she was gritting her teeth and swinging with all her might.

When the body is tired, stray thoughts don't come.

So the body should be a bit tired.

But strength and stamina that transcend humans don't easily tire.

So harder, faster, stronger.

The sound of the sword tearing through the air was loud. The wind pressure created by the sword swept across the training ground floor, raising dry dust.

Yet there was still energy left for stray thoughts.

\textit{What on earth is inner power anyway?}

\textit{If Qi really existed, why did the martial arts world disappear and martial arts not exist in that other world? If there were such superhumans, martial artists wouldn't have all died from bullets.}

\textit{No. Don't think stray thoughts. Yes. Let's count numbers.}

Counting numbers is the best way to focus on something.

So one number for each sword strike. One two three four five six seven eight nine, one.

Nine bundled as one, two, three, and then ten bundles of ten was one after nine.

From the start, it wasn't about wanting to know how many strikes, just wanting to empty the mind.

So it's rather better.

\textit{How many double digits was this?}

\textit{Two hundred? Three hundred? Did I count three hundred earlier?}

Counting numbers naturally puts more power into even simple movements.

Repeating the use of power, even a body that transcends humans gradually becomes out of breath.

Then inner power naturally rises.

Qing forcibly closed and suppressed the internal organs that were trying to sneak in some work.

\textit{Read the room, will you? A person is trying to look a bit tired here.}

How much time passed like that.

"Huff, whew, I'm a bit out of breath."

She had clearly come out to the Wucheon Pavilion training ground to swing her sword before sunrise, but now it was dark all around with only bonfires lit widely.

Now her heart was pounding and her limbs felt like they were about to break off, finally feeling like she had gotten some exercise.

It was something that would have terrified anyone who heard it.

Because it was the words of someone who had swung a sword for two and a half shichen straight without taking a single breath, without using inner power.

Just as Qing was wiping off the sweat that had soaked her:

"Is that the Three Powers Sword? If the human technique is thrusting, it must be the southern style Three Powers Sword."

Qing brightened and welcomed Gong Sun-Yaoyi.

"Yi! You woke up! I thought you might never wake up. Do you know how much time has passed? Are you okay?"

"Did I, did I lose consciousness for that long? How long has it been? Three days? Four days?"

Gong Sun-Yaoyi asked hurriedly in surprise.

"I'm joking. Only half a day has passed. Does your head hurt?"

"How did you… Was I making a pained expression?"

"No, you drank so much alcohol, of course your head would hurt."

"Ah… It feels like it's being stabbed with an awl. You say of course, is it normally like this?"

"It's different for everyone, but if you drink strong liquor for the first time and pour it in like that, of course your head will hurt. That's called a hangover."

"Ah. So this is what a hangover is…"

It seems she had been deliberately hiding her pain in front of Qing. Now that she was told it was normal, she finally showed it, with her right eye twitching, suggesting she had a migraine on that side.

"If it hurts, you should say it hurts. Don't pretend to be fine."

"But, you'll worry, won't you?"

"It's better to worry. What if there's really a problem and you collapse later? If I was next to you and didn't know, how upset and angry would I be?"

These were the words of someone who always pretended to be fine in front of others.

However, it's nearly impossible for people to view themselves objectively, so it's hard to blame Qing.

At this, Gong Sun-Yaoyi listened well.

"Ugh, it hurts a lot, a lot… Is there any way to deal with this?"

"Drink a lot of water. Ah, not tea. Unless it's fruit tea. And eat a lot of sweet things. If you drink sweet water, it solves both at once, so um, should I ask for some fruit tea?"

"My stomach doesn't feel good either…"

"Then, we need to do some hangover recovery. I should ask for some clear soup with plenty of fruit tea."

"Do I really have to eat something now?"

"You have to eat to feel better. Come on, let's go."

Qing grabbed Gong Sun-Yaoyi's hand and dragged her along.

Gong Sun-Yaoyi let herself be pulled along, closely examining the hand holding hers.

After Qing asked the Wucheon Pavilion maids, a table was quickly set not long after.

A characteristic of Chinese cuisine is quickly frying or boiling pre-prepared ingredients.

In China, stir-frying isn't much different from deep-frying, so they stir-fry by pouring oil into a wok and frying.

Gong Sun-Yaoyi slurped the clear soup boiled with lots of dried fish, opened her eyes wide, and unconsciously let out a melting sound.

"Huaah, wow, this, it's really good. My stomach is, haah, feels good."

"See? After passing out from drinking, clear soup is the best. Hmm. Or spicy soup is good too. As long as it's not greasy, hmm. Come to think of it, I really crave it."

Before entering Jianghu, Qing used to have a habit of buying a famous chain's cheeseburger and throwing it on her desk before sleeping after drinking a lot.

When she woke up with a hangover, eating that for recovery was perfect.

Come to think of it, it doesn't seem particularly difficult to make, so I should ask to have some made later, she thought.

Thinking this, Qing also scooped up some soup and was about to bring the bowl to her mouth when she paused.

"Ah, I should take this off. It's stuffy."

Qing took off her face veil and put it down.

While at it, she also undid her hair, and her soaked hair drooped like seaweed.

At this, Gong Sun-Yaoyi froze in place, awkwardly holding her bowl.

Qing smiled seeing this.

"Hm? Why. Because I'm pretty?"

Gong Sun-Yaoyi nodded, still holding her bowl.

Then she stared at Qing's face for a long time.

Unfortunately, it was right after sweating a lot, so with her hair sticking to her face, it was an irresistibly seductive beauty.

Gong Sun-Yaoyi was dazed like that, then quietly asked:

"Um, when you do this hangover recovery thing, do you normally feel your face heating up? Like you've soaked your whole body in the soup and come out, and also, my heart is pounding…"

At this, Qing's expression became serious.

\textit{Yi, could she…}

\textit{Have high blood pressure? Or angina?}

"We should have Lan-Ah take a look at that."

"But why do you hide your face? When you're this pretty. It's such a waste, isn't it?"

"Well. It's annoying when men flock to you. Well, I saw today they flock even when it's covered. Ah, I'm not badmouthing your brother."

When people came to greet her saying she won the drinking contest, there were more than a few who looked her up and down with creepy gazes.

Many even threw blatant stares, thinking that since Qing's eyes weren't visible behind the veil, their lecherous gazes weren't visible either, the fools.

They should be the ones wearing veils, even though the person wearing one can still see in front of them.

"Ah. I understand. Still, it's a shame."

Gong Sun-Yaoyi understood immediately.

It was a beauty with that much destructive power.

"I'm not going to hide it forever anyway. And at this point, it feels a bit childish to reveal my face now, like I'm not some top-class chef but doing some kind of cheap trick."

That wasn't the intention, but at this point, taking off the veil would be like painting gold on her face saying "Actually, I was a beauty all along."

It had become even harder to reveal her face, you could say.

"I was thinking we could spar together after eating, but with your head shaking, it would be hard with the headache, right?"

"No, I'm fine. It's what I always do anyway…"

"You're not fine. Who on earth exercises with a hangover? Unless you're running while still drunk. Hmm, they've put lanterns on the canal in front, want to go see that together?"

At this, Gong Sun-Yaoyi's face bloomed.

"Ah! Yes. Thank you. Thank you. How can you say such grateful things again…"

As she thought this, she wondered if she had done well to unknowingly reveal her embarrassing inner thoughts.

Originally a kind, gentle, thoughtful, good-hearted, compassionate, and even inclusive friend who was now even pretty on top of that, too good to be true.

But somehow, the distance seemed much shorter than before. Like she was coming much closer.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After being subdued and dragged away, Murong Zhuji passed out drunk.

Some drinkers have a convenient brain structure that completely forgets the shameful things they did while drunk.

But martial artists' brains weren't so weak, so even if they lost their reason and acted out while drunk, they had to wake up with those memories fully intact.

So Murong Zhuji's heart broke again.

The heart that had been patched together with vengeful poison burned again, breaking into even smaller pieces than before, no, ground into fine powder.

"Uwaaa! Aaaah! Aaaaaaah! Aak! Aaaak! Kuaaaaaah!"

Only the pillow that swallowed her sad screams suffered.

If it was sadness before, this time it was closer to despair, a desperate scream.

And Murong sounds are heard by Murong Jun.

"Sister! Sister, what's wrong again! Sister!"

"Uwak, what do I do! How can I show my face after this!"

She had pulled out her fake breasts and thrown them away in front of all those people, revealing Murong Zhuji's true identity to the world.

Moreover, she had even guaranteed it herself, shouting at the top of her lungs that she had none at all.

A stream of dew flowed from Murong Zhuji's unusually large eyes.

"Wh-what do I do? Isn't my marriage prospects all gone? Jun'er, what if sister has to live alone forever? Where in the world is there a man who would like a flat-chested bitch?"

"It's okay! Then I'll stay with sister! We're family!"

"Ju-Jun'er!"

Murong Zhuji hugged her brother fiercely.

Murong Jun thought his sister's ribs pressing against his temples hurt a bit, but he could judge for himself that he should endure it for his sad sister.

It was all thanks to the teachings of the beggar sister, no, Sister Qing.

Just think one more time before speaking whether what you're about to say might be hurtful to the listener.

Telling his sister who was sad about her small breasts that her bones were hurting him seemed like it would be a very, very bad thing to say.

With her cute younger brother's warm comfort, Murong Zhuji overcame her despair a little.

Moreover, despair was familiar to Murong Zhuji.

Every chest she saw was a continuation of despair for Murong Zhuji.

"Right, family, because I have family. And I have friends too."

At least she hadn't made a complete verbal blunder, thanks to her gracious friends who had covered her mouth just in time.

It was a bit frustrating to see them pretending to understand because they had at least a little, but still, weren't there friends who shared the same pain, just different in depth?

Of course, if Murong Zhuji's pain was 100 points, her friends would be about 8.9 points, so no one could truly understand her sorrow.

Fire lit in Murong Zhuji's eyes.

"I can't forgive her. I'll never forgive her."

"Sister?"

"That bitch, I can never forgive her. How could she do such a terrible thing, digging into someone's most painful wound? Jun'er, don't you agree?"

These were the words of Murong Zhuji, who had put on a grand self-harm performance.

"That's right! It's terrible!"

"Not enough. Say she's a terrible bitch. Quickly."

"Terrible bi- bitch!"

"Bad bitch, evil bitch, worst scum under heaven, hypocrite putting on airs…!"

"Do I have to repeat all that?"

"Just say bad bitch, will you?"

"Bad bitch!"

"Yes. She's a bad bitch. And an eye for an eye, a tooth for a tooth. She touched my weak point, so I'll reveal her weak point to the world too."

\textit{Since she's a bitch who hides her face because she doesn't want to show it to others, revealing it in front of everyone at the Dragon-Phoenix Assembly would be the same revenge.}

\textit{I didn't want to go this far, but.}

\textit{I was going to let it go with just making her properly drunk and crawling on the floor in front of everyone.}

Then Murong Jun shouted:

"I'll help too! What should I do?"

"No. Jun'er doesn't need to get involved in this dirty business. Just, will you stay by sister's side? Even if the world points fingers, you'll take sister's side, right?"

If it's about lifting the veil of a woman who hides her face, it was close to sinking to the same level.

It would be a heinous act deserving universal condemnation, being pointed at as a very, very evil bitch who digs into others' painful wounds.

But thinking that way makes it even more unforgivable.

\textit{That bitch did the same thing but pretends to be benevolent and becomes a noble heroine, while why did I become a pathetic bitch whose small breasts were even fake?}

Murong Zhuji's insides burned fiercely.

At least it wasn't expelled as screams, thanks to her comforting brother.

"Yes! I'm absolutely on sister's side!"

"Yes. Our Jun'er. Now I really have no one but Jun'er."
