\chapter{Dragon-Phoenix Assembly (13)}

Originally, they said the tens of thousands of lanterns floating at the starting point of the huge canal in front of Kaifeng Prefecture was a spectacular sight.

However, construction had begun to set up a martial arts stage by floating boats on the canal and connecting planks, so unfortunately that sight couldn't be seen.

Still, they continued to float lanterns on the tributaries of the canal.

There was fun in watching the lights floating gently, so Qing linked arms with Gong Sun-Yaoyi and took a big lap around.

By the time they finished, the moon had already risen on the other side, reaching the end of the Hai hour.

"Miss Ximen, today was really enjoyable. It was my first time drinking alcohol, and it was even better drinking with you. Hangover recovery? The hangover recovery was good too, and the lanterns on the canal were so pretty. It was even better walking together. If, if it's alright, if you could spend time with me like this again, this humble one would truly consider it an honor for three lifetimes and cherish it in my heart forever-"

"Calm down. It's late, where would you go dangerously? Stay over tonight."

"But wouldn't that be rude?"

"There aren't any other guests besides me, so what's the problem."

And so Gong Sun-Yaoyi set foot in the Wucheon Pavilion again.

Wearing guest sleepwear and lying in bed, her heart swelled anew. It wasn't a friend's house, but it was the first time sleeping somewhere similar.

For Gong Sun-Yaoyi, whose entire life had been nothing but training, every experience was a first.

Perhaps because of this, even lying in bed, sleep wouldn't come.

Of course, if Qing heard, she'd say it's natural not to be sleepy after passing out drunk for half a day.

Gong Sun-Yaoyi pondered while lying down.

\textit{Maybe I could ask Miss Ximen to talk together now? Would that be too much?}

\textit{It's my problem that I can't sleep, Miss Ximen must be very tired today.}

\textit{But it's my first time sleeping at a friend's place, isn't it too disappointing to just let it pass? Moreover, who knows when I'll have such an opportunity again.}

\textit{If I ask, kind Miss Ximen would probably agree, but she must be tired.}

\textit{What if she thinks I'm tactless for asking?}

It was the greatest dilemma of Gong Sun-Yaoyi's life.

While she was wavering, unable to do this or that:

The door opened slightly, and a face peeked through the gap.

"Miss Ximen? Do you have something to say?"

"Hmm. Well. Can I sleep together? The room and bed are so big, being alone is a bit…"

Just as Gong Sun-Yaoyi was about to answer, Qing hurriedly added:

"I don't mean anything else, it's just, what was it, I heard in Zhongyuan that sleeping together in one bed with a friend is true friendship or something? I've been a bit skeptical lately, but anyway it's not a made-up story."

Indeed, there was a saying about 'same bed, different dreams', referring to having different thoughts in the same situation.

They specifically expressed this as having different dreams in the same bed, meaning even close friends can have different opinions.

This was also evidence that friends sleeping together was a common thing.

Qing's eyes visible through the door gap rolled around, checking the reaction.

"Um, is it okay if we sleep together? I'm not usually like this, but today I feel especially…"

"Of course. I was actually wanting to ask the same thing. Please come in."

"Alright! This is what having a friend is all about."

Qing giggled as she came in, climbed onto the bed and burrowed into the blanket.

The lump under the blanket wriggled closer, and suddenly Qing's head popped up right in front of Gong Sun-Yaoyi's nose.

"Ahh. This is nice. It really is better having someone here. You're not uncomfortable, are you? If it's uncomfortable sleeping with someone, we can't help it."

"Not at all. I really wanted to sleep side by side with a friend too. I'm grateful you suggested it first."

At this, Qing smiled affectionately.

"I'm glad you say that."

Then she wriggled around under the blanket for a bit, and before long, the sound of steady breathing filled the air.

Although it was Gong Sun-Yaoyi's first time seeing someone else sleep, it was also her first time seeing someone fall asleep so quickly.

Only Gong Sun-Yaoyi, who couldn't sleep because she had slept plenty during the day, felt a bit resentful.

\textit{We're finally sleeping together, but you won't even talk to me…}

How much time passed like that?

Suddenly, something heavy slid onto her.

"Mi-Miss Ximen? Y-your leg…"

Having exhausted her body and walked around all night, Qing had completely passed out on the comfortable bed, so how could she hear?

Soon Qing went 'Mmm' and shifted, then leaned her whole body against Gong Sun-Yaoyi.

This really is like sisters.

Gong Sun-Yaoyi smiled warmly and was about to hug Qing, when suddenly her body stiffened at the sensation on her fingertips.

"U-um. Miss Ximen? W-why, why are your clothes…"

But Qing was in a deep sleep.

Only Gong Sun-Yaoyi remained stiff all night, unable to control her pounding heart.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tang Lan-Ah climbed the Wucheon Pavilion.

She had heard that Qing was staying at the Wucheon Pavilion, so she planned to eat lunch together and go to the Dragon-Phoenix Assembly.

Intending to surprise her, she climbed to the top floor, where she saw a Wucheon Pavilion maid blocking the corridor door.

"Is Qing'er inside?"

"It seems she's still sleeping. Shall I announce your arrival?"

A sly smile spread across Tang Lan-Ah's lips.

"Sleeping? Hehe, then I should wake her up?"

"Um, guest. If you enter rudely while the honored guest is sleeping…"

"I'm Qing'er's best friend, you know? Ask Qing'er later. She might get angry if you blocked her friend from entering."

"She doesn't seem like that kind of person, but…"

Still, the maid didn't move aside.

After all, she couldn't let in an unauthorized guest, even a woman, to the honored guest's room without permission.

"Ah. I don't know. Move. I'm Tang Lan-Ah. Blooming Poison Flower Tang Lan-Ah. I, the legitimate daughter of the great Sichuan Tang Clan, am going in, how dare you block me?"

"Ah. So you're Miss Tang Lan-Ah, I was told in advance to let you in if you visited."

The maid's expression brightened.

She thought it was a troublemaker, but it wasn't.

It's fortunate Qing had said something in advance, because in fact, she was a troublemaker.

"Where's Qing'er, ah there are the shoes. Shoes."

Tang Lan-Ah's expression turned vicious.

There were shoes, but two pairs.

Qing naturally has two feet, and she doesn't have a habit of wearing shoes on her hands, so two are Qing's, but the other two aren't Qing's.

At least they were round women's shoes, which was fortunate.

"What's this, who is it? How dare they!"

Tang Lan-Ah flung the door open.

Qing normally has sharp ears, but when she judges a place safe, she just sleeps obliviously.

The luxurious guest room at the top of a magnificent building inside the Wulin Alliance was a very safe place.

Gong Sun-Yaoyi also has sharp ears, but she had just fallen asleep at dawn after staying up all night with her eyes open.

Tang Lan-Ah's eyes flashed fire when she discovered two heads stuck together on the bed.

"You bitches!"

Tang Lan-Ah yanked the blanket.

Given their sleeping attire, the sudden wind on their skin made Qing frown and open her eyes.

"Ah, my blanket… What, it's Lan-Ah. Give me the blanket. It's cold. Well, it's not really cold. But I like being warm."

"You, you! How could you do this to me, Qing'er! When I ask to sleep together you make all kinds of excuses to avoid it! And then you bring another woman into your bed!?"

"Isn't that line a bit much? Someone might think I was having an affair."

"How can you say such things!"

"Yelling so loudly in the morning… Ah, the sun's up."

Qing sat up and scratched her messy hair. Then she felt around for the crumpled sleepwear under her hips and roughly put it on.

Then she burst out laughing at Tang Lan-Ah's vicious expression, still breathing heavily and glaring.

"What? Were you that upset? Then, let's sleep together tonight. No, this is perfect. Let's just stay together for a while. The lodgings are so big, it feels empty using them alone."

"Huh? Really?"

"Mm. Sorry, but you'll see your family every day when you go back to Sichuan anyway, right? So while we're in Kaifeng, stay with me a bit. Um, do you not want to?"

Tang Lan-Ah's mouth gaped open uncontrollably, then suddenly she tilted her head.

Qing's slightly furrowed eyebrows and expression looking up with some anxiety were strangely unfamiliar and novel. What, in the world, is Qing'er checking my reaction right now?

Then Tang Lan-Ah's cheekbones ascended.

\textit{Right. Of course she'd feel sorry for bringing in such a bitch and leaving out her best friend.}

That was her train of thought.

----

Gong Sun-Yaoyi left saying she had to go to her family since she stayed out overnight, and Qing linked arms with Tang Lan-Ah and entered the Dragon-Phoenix Assembly hall.

They made their way through the rising stars greeting her as the world's greatest drinker, seemingly looking for someone, until they stopped next to Nan-gong Shencai who was pouring out praise for swords.

"Oh, Sword Friend has come."

"Yeah. But, do you want to come spar at the Wucheon Pavilion? Lately I'm not sure about swinging my sword. So I was thinking of swinging it for a while."

"Oh! Has Sword Friend finally gotten serious about swords? For such a joyous occasion, this Sword Brother should roll up his sleeves and help. What do you say, Sword Brother? Shall we have a match right now?"

"A bit later. I'm not planning to come here again until the martial arts competition. Today I just came to greet people before leaving. Want to go together when I leave?"

"Excellent! I was just itching for a match, my hands were tingling. No, this isn't the time. I'll be warming up in the back, so find me when you're ready to leave? Ah, I should order some wooden swords to be delivered to the Wucheon Pavilion. You're prepared, right?"

"Of course."

Qing smiled brightly and held out her scabbard.

Sword Friend bumped his sword against hers and ran out with excited steps.

Tang Lan-Ah clicked her tongue beside her.

"Is sparring that fun? He's not in his right mind either when you look at him."

"Isn't it better than being into other things?"

Then she scanned the floor looking for familiar faces again, and found Changbin raising his voice among disciples wearing various types of Daoist robes.

"Ah, this really ruins the taste of alcohol. There's not a single woman to be found. What is this, just sweaty men gathered together? Since ancient times, alcohol is best when served by women…"

"Is that so? Here. Have a drink."

"Hmm. You've come."

It was still awkward formal speech.

Qing burst out laughing.

"I'm staying at the Wucheon Pavilion, you know? I was thinking of gathering friends to spar and spend time together, so Changbin should come over too."

And after telling him not to let this pass as it was an elder speaking and to make sure to come visit, she set out to search for acquaintances again.

Come to think of it, wondering if Xiang'er hadn't come, she looked around, and strangely there were no women to be seen in the hall.

"What's this, is it the Azure Dragon Association today? There are only men?"

"I didn't hear it was being held separately today? What's going on…"

Tang Lan-Ah also trailed off, saying it was strange.

And the reason could be known right away, because when they went up one floor, all the women were gathered there in a commotion.

What on earth is going on, is a master confectioner making sweets on the spot or something? As they stood confused on the landing, suddenly there was a loud rumbling of footsteps.

Then the women parted left and right, and the jade face of the world's most handsome man appeared with a flourish.

"Are you here now, Qing? As expected, you probably lazed around until the sun was high in the sky. Still, it's good to see your face."

Strangely, he greeted her warmly, even calling her name which he usually avoids with disgust.

Usually he only ever called her 'you'.

At this, the women's gazes converged on one point, with a fierce aura as if they would pierce through Qing's face veil.

At the same time, there was a clamor of whispering.

-Qing, he said Qing. Did you hear?

-I didn't hear. I didn't hear. I didn't hear.

-He's calling her by name. By name. Is that possible?

-He said it's good to see her face!

-Friend, they must be friends. I don't know. I didn't hear.

Since Qing's hearing was beyond ordinary, she could clearly hear the whispers amid the ominous atmosphere.

\textit{Ah. This is a bit burdensome.}

\textit{Come to think of it, isn't this how bad rumors that block a friend's marriage prospects spread?}

"So Young Master Peng has come. Don't you usually avoid such gatherings?"

"Still, I should come at least once. Yes, did you get back safely yesterday? After you suddenly left, I felt uneasy. You didn't look well, how are you?"

At this, screams erupted.

Of course, asking if she got back safely yesterday meant they were together yesterday.

Now as killing intent rose among the women, Qing's eyebrows twitched, revealing her uncomfortable feelings.
