\chapter{Dragon-Phoenix Assembly (11)}

After throwing the completely passed out Gong Sun-Yaoyi into the Wucheon Pavilion guest room, Qing diligently went out again.

With each step, she felt waves crashing in her stomach, sloshing around with how much alcohol had filled her belly.

Indeed, if you're going to fill up, it should be with food, filling up with water makes it hard to move.

After leaving the Wulin Alliance main gate and walking for about half a shichen asking directions, a familiar sign caught her eye.

Zhonglin Inn.

Among China's administrative provinces, there were regions that claimed to be the center (Zhong) of China and took pride in it, and Henan was one of them, so there were many shops with 'Zhong' in their names.

Entering, she saw Peng Daesan sitting at a table by an open wall, wearing a bamboo hat pressed down.

Qing briskly approached and sat down on the opposite chair, squashing it with her butt.

"I came to leave a message in case you came, but you're already here? Nothing to do?"

She thought Peng Daesan might come looking for Qing later and come up empty.

So she was planning to slip some coins to the innkeeper and ask him to relay that she had settled in the Wucheon Pavilion.

\textit{Well, since he covered his face, he's gone wild, seems he's gotten a taste for going around hiding his identity.}

"Did you greet the Alliance Leader well?"

"Yeah. I even got a really fancy lodging. Called the Wucheon Pavilion. It's awesome, really."

"The Wucheon Pavilion?"

Peng Daesan didn't hide his surprise.

The Wucheon Pavilion was a guest house for only the highest honored guests of the Wulin Alliance.

These highest honored guests referred to kings and high officials, so it was a facility that had hardly been used since the unwritten agreement of non-interference between government and martial arts world.

"You must have made quite an impression on the Alliance Leader."

"Elders always like me. And peers like me too? Kids go crazy whenever they see me, so I can say I'm loved by everyone."

"You should leave out the peers. The more they know you, the more disappointed they get, and it's surprising that there's even more to be disappointed about."

Peng Daesan made an uncharacteristically humorous joke.

"Hmm. I don't know why my friends are getting harsher. Zhuge too. Lan-Ah too. Even Sword Friend, his words are starting to be eaten by the mouth rather than the ear."

"Do you really not know?"

If he were to list them: violent eating manners, rude speech and endless joke-making, attitude that doesn't know how to be serious.

Above all, while butting into others' business without boundaries, drawing a clear line when it comes to her own business.

But Qing-

"I don't know. But I'll keep not knowing, so you don't need to explain."

She just doesn't try to know, so she'll keep not knowing.

Besides, aren't people supposed to praise each other when they're less close and criticize each other when they're very close?

You could say we've become close enough to be uninhibited, so it's time to start pointing out each other's flaws.

"That's too bad."

"You look like you have a lot to say, just spit it out. I won't change even if I hear it anyway."

"You're boldly talking nonsense."

"See? This is what I mean. Getting harsher and harsher. Should I throw away old friends and make new ones just to hear nice words?"

"You hear that you're talking nonsense because you say such things."

"What, can't I even joke? Ah, come to think of it, I saw that person at the Dragon-Phoenix Assembly today. Brother Chao."

Qing continued, giggling.

"My goodness, if you're going to seduce women, you should do it properly. He goes crazy saying everything is pretty. The funny thing is, he said everything except my face. Does that kind of talk actually work? Compared to him, the Gong brother is a real hunter of women's hearts."

"The Gong brother?"

"Ah. Yes, Gong Sun-Yaoyi's younger brother is really born to seduce women. He follows around diligently, taking out handkerchiefs when you sit, setting plates, preparing utensils, cutting food just right to eat. He looked like he'd even feed you if you asked."

Peng Daesan's eyebrow twitched.

Qing couldn't see it because of the bamboo hat, and Peng Daesan couldn't observe his own eyebrow.

So it was an unconscious manifestation that even he didn't notice.

"Hmm. So, did you like it?"

"It's comfortable, but still a bit burdensome. You can see he's determined to seduce. It seems he doesn't even try to hide it from the start."

"Ha. You must have shown your face? Like you did to me?"

"No? He's like that even without knowing this beauty. I heard that Yi, I mean Miss Gong Sun-Yaoyi, has only me as a friend, so it seems he wants to make me family. Hmm. As a younger brother it's admirable, but as a man, it's a bit, impure?"

"Hmm…"

"What's with the ‘hmm'?"

However, instead of answering, Peng Daesan answered the question with a question.

"So, was that guy handsome?"

"Who? The Gong brother? He's very handsome. No, he's more pretty than handsome, with a delicate, slender frame? But even if you put aside looks, he says things that give you goosebumps whenever he opens his mouth."

"Hmm."

"The women just faint over him. Something about a white qilin. I heard the Phoenix Association women whispering about a warm white qilin and cold black qilin or something. I guess San is the black one."

"Hmm."

"No, have you been just breathing this whole time? When someone talks, you should at least respond."

"Respond."

Peng Daesan seemed to think for a moment, then asked as if talking about something completely unrelated:

"So, did you like that guy?"

"Well, as a friend's brother he passes. Is it a common idea to follow around a veiled woman for his sister's sake? What does he think is under the veil? In my case, you could say it's a big jackpot grand prize."

"That's probably not all."

"Huh? What isn't?"

"That he's doing it for his sister. He probably didn't approach you just for his sister's sake."

"Then?"

"The Gong Clan has a long-cherished wish they've been grinding their teeth over, so he was probably tempted by your status and connections too. Aren't you close with the elders of the Nine Sects and the Five Great Clans?"

"You're saying his motives are impure? But that sounds a bit off? Even with my face covered, anyone who approaches me is after my background?"

Then Peng Daesan's bamboo hat slowly rotated left and right.

"Just getting their name on the Ten Great Clans isn't the end, they need to establish relationships that didn't exist before. To reclaim a surname lost once to treason isn't something possible without considerable power. They probably decided to bring in an in-law at this Dragon-Phoenix Assembly."

Hearing this, it made sense, as Gong Sun-Yaoyi had completely buried her childhood and youth in training.

It seems unlikely that clan people who didn't look kindly on that would leave the heir alone.

In fact, Peng Daesan's words were correct.

An heir can't be free from a clan's long-cherished wish passed down through generations, so from Gong Sun-Tianri's perspective, a woman's beauty or appearance wasn't of any interest at all.

Since her personality seemed good too(?), her background was actually tremendous, and above all, it could be good news for his pitiful sister who had devoted her entire short life to martial arts.

"If he's kind to every woman he meets, there must be a reason. Unless he's pathologically fond of women like Brother Cao."

Qing chuckled.

"Well, what's wrong with that? If that's his purpose, he'll treat his wife well too. Whatever the motive, if they're happy together and live well, that's fine. Though it's not to the extent of comparing him to Brother Cao. That person was quite creepy."

"Trying to seduce a woman for strategy, isn't it all about the purpose in the end? If he marries like that and the background disappears, would he throw her away?"

"Huh? What's this. That's for the people involved to figure out, it's not for us to discuss, right? Ah. Right. Do you know Miss Xue Iri? Miss Xue Iri the Ice Snow Flower."

"Even if you say people can get attached and live well through strategic marriages, that's just what elders who are after benefits say, wouldn't the people involved be unhappy?"

"Hmm. San, your views on love are surprisingly conservative in some ways. But, are you still continuing that conversation?"

Originally, conversations should flow, and if you forcibly hold onto a topic and keep talking, it just leads to arguments like stagnant water rotting.

Qing had shifted the topic to Brother Cao once, and then to the Ice Snow Flower, but the strategic marriage talk came up again and again.

It seems like he might have something bottled up.

"Why. Is your clan talking about a strategic marriage? It is one of the elders' duties to nag and pester about marriage."

"Marriage in the Peng Clan is entirely up to the individual. It might not be the case for other clans. Besides, well, they probably don't worry particularly."

"Ooh, what's this. Confidence that you can grab anyone and marry anytime? Well, it's not wrong. Come to think of it, Chaolei doesn't seem to be nagged either. What, then, is San not marrying too? You hate women, right?"

"That doesn't mean we can leave the position of clan mistress empty."

"True. That's right too. Well, don't worry. They say even straw sandals have pairs, a woman who likes you for yourself, not your face, will appear for San too."

"Rather than waiting for that, well. No. More than that, what about you? Even though you say it like it's about others, have you never thought about marriage?"

At this, Qing waved her hand.

It was an attitude of don't even bring up such talk.

"Don't say such things. Can't you see? San, Sword Friend, Zhuge, Changbin. They're all friends far from women, right? If someone acts like a man towards me, ugh, just thinking about it is so awkward I could die."

"Hmm."

"Besides, right now I'm too busy taking care of myself to think about such things. From the start, um. Yeah. That's right…"

Qing's voice sank.

It had already been five years of Jianghu life.

Now she didn't even think of those convenient modern civilized things except when seeing dirty toilets, so it seemed she had truly adapted properly.

Moreover, now, yes. It was an enjoyable life.

Perhaps even more so than life before entering Jianghu.

It was so enjoyable that she had forgotten all this time.

But, how long will this time last?

What if, right now, she opens her eyes thinking 'This is a familiar ceiling'?

What if it just concludes as a grand dream dreamed one night, a secret memory kept to oneself?

And then her mind went completely blank, unable to think of anything.

Qing just absentmindedly fiddled with her fingers, interlocking and unlocking them, scratching her innocent nails, rubbing her palms together, gently feeling the table…

Before she knew it, her palms were damp with sweat.

It was a characteristic of anxious people.

"Hey, Qing? What's wrong?"

"Oh, oh. Yeah. A bit. What were we talking about. Hmm. Yeah. It's a bit like that. I'm a bit like that."

"Are you alright? You seem to be in quite a bad state right now. If there's any problem-"

"No. Yeah. No. I'm fine. Somehow. Yeah. No. I think I should go in first today."

"…Are you okay?"

At this, Qing let out a long breath, whoo.

Human hearts are incredibly complex, so when there's something you want to avoid, you sleep.

Those ancient big-nosed people considered sleep and death brothers, because the only moments when people completely forget their worries and feel peace are when they're asleep or dead.

So Qing kept sleeping.

She slept after eating, slept when she had time, and slept again at night.

When she wasn't awake talking with friends or stuffing something into her mouth to chew and swallow, she just closed her eyes.

She shouldn't have done that.

She should have been swinging her sword during that time.

Even the first crisis was just luck following her, what nonsense about transcending the Peak Realm.

First get rid of this fucking status window, then you can sleep from then on, right?

This status window thing is like that too.

Doesn't it usually tell you what to do?

If you just throw someone into a corner of Zhongyuan and say, "Yeah, go do whatever you want" and abandon them, how am I supposed to know what to do?

So it's no wonder it's called fucking.

Qing, with a pale complexion behind her face veil, clenched her trembling hands tightly to suppress them.

"It's just, a bit complicated. I guess I've been a bit lazy lately. I'm thinking of swinging my sword until I'm exhausted and then sleeping."