\chapter{Legacy (4)}

Qing leaps through the distorted space using the Nengpa Mibo's formation technique.

And there standing behind a nameless high-ranking official was Qing.

But seriously who else other than Qing could pull off such a miraculous skill?

In other words if Master Fan Yue wanted to follow he would either have to plow through the officials blocking his path or hope they'd step aside and let him through.

Master Fan Yue chose the former charging ahead and breaking through without hesitation.

He burst out like a Murder Chariot cleaving through the unarmed officials akin to a giant chariot rolling downhill with no brakes.

The issue was that raging chariot was heading straight for him.

A flying Murder Chariot!

In an instant the figure of the Old Martial Artist who kicked off the ground in a straight line filled his vision.

Qing immediately hit the ground.

Though rolling was disgraceful for a warrior who wouldn't roll in the face of immediate danger?

``Wak! Waaak! Uwack!''

However the noise he made was a bit ridiculous.

It wasn't terrified screaming.

It was a strategy to distract the enemies a habit ingrained from years of real combat.

In the whirlwind of the world around him—ceiling walls doors pillars the floor old men and flashing legs—Qing's left arm slammed against the unforgiving floor of Huanggu Hall ricocheting him off with the intense recoil of his roll.

Bang! A deafening crash echoed as if an explosive shell had just detonated sending up clouds of dust from the floor splintering the wooden structure of Huanggu Hall and peppering his whole body with countless debris.

``Kraah!'' ``Help! Help!'' ``Your Excellency!''

The Huanggu Hall filled with chaos and screams.

Officials rushed to turn around yelling and stumbling over themselves; some tripped and in the chaos others were stepping over each other.

``Your Excellency! You need to get out of the way!'' Even in the commotion those mindful of their superiors huddled together and helped each other up trying to ensure everyone was okay…

These high-ranking officials managing the country were no different from the fray around them in this official disaster.

Deng—!

The sound of a colossal bronze bell added to the chaos.

With a thud Fan Yue's body lifted and flew away.

Yet his form was straight sword held high intense gaze fixed directly on Qing.

Qing quickly got back up and wildly extended out her hands.

Her posture was flailing hands, slapping at nothingness, frivolous and shabby.

But onces she added the dramatics of blood-red handprints, anyone would be left in awe of the might of this Divine Skill.

With the wild splashes of blood a substantial palm form came to be.

Qing strained against the ground and pressed both hands forcefully outward.

Her extended palms shot forward.

And then from there surged the gigantic blood-red handprint of the Blood Mi-ryeok!

This was an extraordinary skill from Master Mi-jong of Xizhang, the Great Handprint.

Master Fan Yue's sword turned back.

It was like he was unaffected by the enormous judgment of the Blood Mi-ryeok aimed at him taking a breath and slicing through the air diagonally.

The preparation and action happened with such fluidity that they melded into one a manifestation of the extraordinary technique of the heart being one with the strike.

In that moment Qing's extended palms aggressively gripped the air.

The massive Blood Mi-ryeok handprint disintegrated instantaneously scattering into smaller handprints that retreated behind.

With a slicing strike the Sword Master's attack cut through the air.

Little handprints surrounded him in a crescent as the sword slipped through the moment—

Qing extended his palms again!

Hundreds of small Blood Seals aimed fiercely at Master Fan Yue's body.

Great Handprint: Seven Layers.

Nothing was lost from the Buddha's will.

And then it happened.

Fan Yue's arm extended upwards and downwards.

Clearly one arm appearing to be present yet not present moved quietly in a gentle arc.

Mysterious yet smoothly natural— the powerful rotation of sword techniques the light rose and heavy fell reversing in a grand cycle rotating in accordance with reason.

The Blood Seals flew out in all directions.

Kaboom! Hundreds of fireworks sounded off.

The Huanggu Hall the grandest battlefield in the Zhongyuan erupted with streams of blood-red energy leaving countless handprints in its wake.

But what in the world was that cheating martial art?

And as for the Buddha catching everything what a load of nonsense—nothing was touching him and all was bouncing away!

If A-mook-hap-rab heard that he would just cackled, 'Since you're not the Buddha, of course you'd get knocked back. But if you really grasped Buddha's level, you'd have turned him into a puddle of blood in an instant', and he'd surely spend this time trying to preach about reaching the Buddha.

Qing extended her palm once more.

Deng! Deng! Deng!

The eccentric sounds of the long-tailed bronze bell rang out energetically overlapping and resonating; it was merely noise that could not come close to that of a bell.

Tathagata's Divine Plam on the right hand, Great Handprint on the left hand.

Invisible rough tension and blood slowly surged forward in irregular beats towards the enemy.

However Master Fan Yue wielded his sword lightly.

Step by step slowly approaching swinging his blade as if chasing away a fly.

But every time behind Master Fan Yue the walls came crashing down with a sickening noise.

The force of the Buddha's Physical Body and Blood Seals was brushed off lightly.

With that one step then another.

Qing's heart raced.

Wow this was the legendary evil spirit of humanity.

``Wait! Shouldn't we talk it out?''

At that Master Fan Yue halted for a moment then chuckled.

It was a fierce smile distracted yet satisfied like a beast revealing its teeth.

``Buddha's Palm and Great Handprint. To see both extraordinary techniques unfold from a single person is truly impressive.''

``Uh um… Ah right, then should we visit Tianzhu? Since we're gathering wouldn't it be marvelous to learn the Buddhist techniques of Tianzhu and use them together as a Trinity?''

With nothing but idle talk Qing started.

Master Fan Yue nodded in agreement.

``That sounds like a smart idea. Let's do it.''

``Oh really? Then I'll go to Tianzhu right now—''

``It's my saying I will go with the Mu-sang-gong. Since I'll have to leave the Zhongyuan one way or another I might as well—''

``Wait! Wait!''

Qing interrupted Master Fan Yue's words.

Fan Yue's eyebrows twitched.

``Why are you cutting off my words? No matter how respected you are the laws of the palace—''

``You are trying to ambush me as you finished speaking, aren't you? Just like now.''

``Sharp-witted you are. Or is that too a specialty of the Mu-sang-gong?''

``Stop that let's just talk okay? Hm? The Mu-sang-gong? I can teach you everything.''

``I already mentioned it before. The Mu-sang-gong was a mystic sect's legacy destroyed in a civil strife long ago possessing incredible power. If we could share the Mu-sang-gong then such a great sect wouldn't have caused tragic havoc through their self-destruction.''

Qing's heart sank once more.

Just like that Heavenly Demon Soul there might be some martial arts that absorbed energy and shared skills.

Does that mean he's not trying to share martial arts but actually intends to kill him?

In that moment Qing's knees buckled.

With knees bent he lay down forming a horizontal position with the ground—a technique called Cheolpan-gyo.

Boom! Fan Yue's blade cut through where Qing's waist used to be.

Ah this old man really fights dirty.

Qing thought as it was something he'd usually do but people can never objectively reflect on their actions.

At the same time Qing's right foot shot up.

Faster than anything in the world his toes wedged through Fan Yue's legs thwack!

Ugh! With the recoil of the protective energy an intense pain surged as if all his toenails cracked throwing Fan Yue off balance and into the air.

Of course Qing's strength lived up to her name as Ximen Qing.

Having turned the great hero Han Xin into the blue-green hero it made sense for the world's greatest champion to bear Qing's name.

So it was natural for the old body to float after a kick to the groin.

However.

Thud. Master Fan Yue landed lightly on the ground.

He felt nothing at all.

Though his bones were close to being shattered between the bones and the impact zone lay an unavoidable deadly flaw that a protecting energy could not guard.

It had to have been a delicate feeling that crushed the bloodlines uprooting the innate mission of his race to reproduce.

This bastard was a eunuch!

The legendary hero was a castrated one! Ah was that too far-fetched?

Anyway!

Of course how could it not be expected?

Qing hadn't even considered it but the one tasked with protecting the princess should obviously have been a eunuch.

``What a disgusting technique you've picked up a bad habit.''

``What if we just talk this out? Even if I die I'm sure we could find a way for you to learn something. After all that ruined sect wouldn't have forced someone to commit suicide claiming they were passing on martial arts.''

``This was a secret sect with rules so strict they wouldn't even reveal their sect's name. Even if there was such a method who would know?''

``Hey let's not—''

``Stalling won't help.''

Once again Master Fan Yue was upon him.

It was as quick as a rain of arrows.

After all Qing's goal was to buy time.

Surely when the Emperor was dragged out there had been orders issued to either kill or capture that guy right?

The skilled figures from the imperial palace would surely swarm to catch this mad old eunuch giving him time to play tricks.

Master Fan Yue was equally aware of this feigning recklessness while persistently attacking Qing.

``Wak!''

Qing shouted loudly as he moved his body.

Rolling and tumbling he sprang up doing cartwheels and scattered to dodge throwing himself forward landing face-first unable to rub his nose and scampering like a beast out.

``Wah wah wah! Oof! Ugh! Stop! No violence! Stop the violence! I hate violence! Eek.''

Sounding off wildly to scatter the enemy's nerves but since his voice was quite delicate it seemed less effective.

In that form yelling and twisting his body back out Qing's appearance was truly the essence of disgrace.

But.

Hmm? What's this? Something's off isn't it?

Feels like he could dodge?

It wasn't exactly that Master Fan Yue's swordplay was ridiculously fatal.

No blindingly fast strike that was impossible to handle nor was it a great blade crushing everything or a heavy sword weighing like a mountain.

No rather it was soft swordplay.

Much closer to a light sword than a killing sword; not aimed at slaughtering the opponent but focused on self-defense and skill cultivation—a genuine lineage of the orthodox path?

Of course there were flashes of rapid strikes meant to cleave through space that made his heart race.

But those sudden strikes didn't quite match the flow of the swordplay as each rushed swing broke the fluidity allowing him to easily dodge and evade.

After which he could finally take a deep breath a fleeting moment of relaxation.

This was after all swordplay.

Qing's face began to show a less desperate look that urgency starting to fade.

In contrast Master Fan Yue's expression gradually stiffened.

Qing's eyes gleamed.

Suddenly Qing's alluring lips moved the sensual flesh inside stirred grazing over his gums weaving sounds from within.

``Master Fan Yue, when was the last time you fought in real combat? No wait. Were you ever in a Life-and-Death Match? Or were you just a blue-blood swinging a sword in safety? Is this really your best?''

At that Master Fan Yue's eyebrows jolted fiercely.