\chapter{Legacy (1)}

'You refused to become Yuansui by your own will and chose Ximen Qing of Wulin instead.'

'So this is how it will be moving forward; if you break this I will treat you as a traitor.'

That was the last statement from the Emperor.

It was a cruel declaration that she were no longer his daughter.

But Qing felt oddly relieved.

\textit{Who wanted to be Yuansui anyway?}

\textit{Honestly if it's not official then it's all good.}

\textit{In fact if the Emperor had wept and clung to me saying 'Come here my precious daughter!' it would have been way more uncomfortable and awkward.}

\textit{I mean it's not like I didn't already feel uneasy with people like the Empress and the guards of the Forbidden City crowding me.}

\textit{I had never aimed to be Yuansui anyway, and I didn't have the slightest desire to be one, so it wasn't like anything had changed.}

\textit{In the end all I got from my encounter with the Emperor was just some unpleasant mission registered in my status panel.}

'Sell Out the Martial World'

\textit{Now I think I understand why the status said 'Sell Out' in such harsh terms.}

The status panel isn't supposed to have emotions like a living being and it hasn't in the past favored any particular faction in the missions given to her.

So why then did such a word come up?

If hypothetically Qing truly were to represent Wulin Alliance beneath the Emperor and act as a pawn against the Sapa then…

That would serve as a warning on how Wulin would see Qing.

A traitor, who sell out Wulin to the Imperial Court.

\textit{So I guess I'd be treated like a swindler.}

\textit{What about that? There's nothing I can do about it…}

But Qing also holds some degree of certainty.

\textit{It's not like my friends or Master would come to resent me as the Divine Maiden Sect disciple.}

\textit{Well you can't be loved by everyone right?}

\textit{Anyway, I gained a whole ten years.}

\textit{I've pushed back the government's martial invasion by a decade; talk about a victory!}

\textit{And since when did I start worrying about missions? Call me a traitor or whatever; honestly Zhongyuan isn't even my country.}

\textit{However apart from that, there's a big concern.}

\textit{If I mention this to Wulin Alliance then I'll be treated like a swindler immediately.}

\textit{Do I have to spill my secrets about my lineage as well?}

\textit{Even without that it's clear that Wulin Alliance was gearing up for a serious showdown with the government.}

\textit{So if it comes down to it it wouldn't be surprising if 'the true power that Wulin does not know'' mentioned by the Emperor shows up sooner rather than later.}

Only after reaching this point did Qing catch on to the Emperor's intentions.

Within ten years, no more than ten years, find a way to elevate to a position representing the consensus of the orthodox Martial World.

After that give everyone a good smack on the back of the head and turn in Wulin Alliance!

\textit{Wow the Emperor really plays dirty…}

And just like that Qing felt a surge of emotion.

\textit{Wait what am I even doing? Why am I supposed to betray Wulim?}

\textit{I'm just an ordinary martial artist, a transcendent one at that, not a hotshot big deal.}

As Qing calmed her whirling thoughts she hears a commotion outside alerting her to the summons from Long Spring Palace.

It was the usual nightly call from the Empress.

Since the Empress had already seated Qing right next door in the inner palace Qing timidly stepped forward into the Empress's quarters.

``They've decided to cancel that horrible marriage talk. That would be obvious! But really, how can you be so uncaring!''

The Empress was fuming all red in the face as she huffed out her angry breaths.

``Um, what's wrong?''

``Don't even start. The Emperor has said he will just leave those fakes and the Tianzhu's trash as is! They should be hung and burned at the very least!''

``Ah… I see.''

The fact that Qing was no longer Yuansui meant she was truly set on discarding the title.

The fake Yuansui had transformed into the real one.

Thanks to the healing fame from Yuansui, the practitioners of the Heavenly Maiden Temple would maintain their status as is.

``What ridiculous face is he putting on?  He may not be able to tolerate the traitors who dared to insult the Imperial Family, but is he afraid of others pointing at him, calling him a foolish father who didn't know his child has been swapped out, so he's trying to hide it?''

``Um, I'm fine really. Actually, um, I'm sorry to say this, but I would prefer to live as Ximen Qing, a martial artist, instead of as the Princess Yuansui. So this may even be a good thing, wouldn't you agree? Don't be too upset.''

``Are you defending that heartless father? Just how naive can you be, you silly girl?''

\textit{Heartless father.}

\textit{Yeah they say he's never liked Yuansui, always scolding her, and that she cowered in front of the Emperor.}

\textit{Ah, I get it.}

\textit{Without a doubt the Emperor was heartless.}

\textit{I don't really care for myself but he was to Yuansui.}

\textit{More importantly, to the people.}

A ruler who doesn't love the people only cares for the grandeur of the world.

Sure the Emperor talked about greatness.

Qing had heard enough about how horrific and terrible Central Plain's long history was all from her unwilling studies.

The Emperor tried to lead a campaign against the Martial World to prevent a great war yet didn't mention the bloodshed that would flow?

Such had been the way of things thus far.

An unfeeling brother who killed his younger sibling to push the Tang family to ruin.

A heartless monarch who despite failing used forest fires to eliminate a rebellious prince while completely disregarding the pain and potential loss of countless people.

Right that's how it goes – a monster was born from a heartless ruler.

As the Emperor spoke about righteousness scapegoats were surely conspiring on how to push their children into the abyss.

But for now I've postponed it.

Who? Why that would be me the transcendent martial artist wielding the Cheonhwa-geom.

I pushed it back for a whole ten years; without me who knows what might have happened.

Looking back on it I must say I'm quite impressive.

Despite that for a heartless Emperor such measures seem logical.

The princess has been swapped?

The Imperial Family's reputation would hit rock bottom.

Plus the Heavenly Maiden sect's monks have roles like the Golden Guards strengthening their role.

Who would take up the Golden Guard's strengthening if we execute everyone immediately?

So if nothing happens the Imperial Family won't lose anything.

And frankly I prefer things this way…

``Come here.''

The Empress casually shuffled to one end of a long chair patting the empty space beside her.

The gesture meant to come lay on her thigh.

Qing hesitates.

It's not like she hadn't done so before but now she feels shy about it.

However there's someone unfamiliar here…?

``Uh Your Majesty? Who was this…?''

``Right you'll remember eventually. You don't even recognize my sister's face?! It's your sister Jo Haryeon!''

``Eh?''

Since when did I have a sister?

Well it's not that I don't have one but one was somewhere in the distant realms of home and the other was just Jang Myung?

But that curiosity quickly turned to surprise.

After all there could be a sister for Yuansui as well.

``Um hello?''

``…Sister.''

That voice made chills run down her spine.

I thought I was used to hearing 'Sister' but it's a different story coming from a stranger's mouth.

``Wait, are you Princess Jo Haryeon?''

``It's Haryeon.''

``Okay.''

What? That's a really vague answer.

Just say if you're Princess Jo Haryeon or Haryeon Jo!

Hey I can just call you ``princess'' or whatever right?

But where have I heard that name before…?

Hmm but hey wow she's beautiful.

Qing has always preferred an elegant delicate beauty with a calm and gentle demeanor a tranquil smile that must also be intellectual.

But how was it that a beauty with such traits in the Central Plain looks like she's suffering?

The first time I met my ideal was a crazed killer without comparison.

The second was all show but had serious flaws as a human.

And now this was the third time.

But this time it seems like she's truly someone with a good nature?

``It's been a while. Even though I didn't realize it was a while.''

``Oh. Yes.''

``Seeing my sister struggle was really something else. You always held my hand and took me to the Garden of Earth.''

Uh how do I respond to that? The atmosphere was really awkward.

``Mother may I have permission to take my sister somewhere today?''

``Sure. Maybe if the sisters talk quietly some lost memories might return. Sleeping together like we used to would be nice too right? Do you remember? Haryeon always was a scaredy-cat and couldn't sleep alone so you would sneak in and sleep together.''

``Um. That's right.''

Though she spoke of things I've never known it just felt awkward to hear.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

``Actually it wasn't me but you who couldn't stand sleeping alone. But I couldn't say it out loud.''

The reason Yuansui snuck into Haryeon's place was that she didn't want to sleep alone.

But Yuansui made it sound like it was for Haryeon's sake.

Because that would resonate better.

Saying she snuck in because she was a coward would just mean labeling herself as a coward.

But Qing finds it mysterious.

Could it be that my inability to sleep alone was because of Yuansui's habits? Was it because I needed someone next to me to fall asleep?

But Haryeon shakes her head.

``No you could sleep anywhere as soon as your eyes closed. You just found it boring to sleep alone and after your daytime nap couldn't fall asleep again so when I looked sleepy and wanted to sleep you'd shake me awake begging for me to listen to your stories.''

``Oh that sounds a bit mischievous.''

At that Haryeon smiles sweetly.

``I suppose I thought you'd be bored. You've always been like that you'd say things like ‘What's fun about reading books? Let's go see the fountain' Oh by the way have you not gone to see that fountain in the Garden yet? It's a must-see every other day!''

``Oh? There's a fountain?''

Qing's ears perk up.

A fountain? As in an elephant!

How can you resist that?

For reference the Garden of Earth was the Emperor's garden also a breeding ground for exotic animals the Emperor's pets.

But they aren't just pets for the Emperor's affection; they were rare animals that have to be raised simply because they were presented as tribute.

``Oh looks like that hasn't changed at all.''

Haryeon chuckles softly.

In that moment Qing finds her mind drifting away as Haryeon's adorable figure catches her eye.

Wow the way she smiles fits perfectly!

Haryeon starts recounting memories of Yuansui sharing how she learned how to make flower crowns and floral wreaths how she rummaged in the Flower Garden putting massive flower wreaths on her head around her neck and even around her waist.

But then Haryeon fell sick due to the poisonous plants she played with.

She was dragged in for lessons but it was only Haryeon who ended up punished while Yuansui could escape.

Whenever she felt bored she would pop by to drag Haryeon out being a super-duper active sister.

The problem was Haryeon was a homebody.

For her every breath outside was too much effort and by the time she went out once a day she didn't want to step out again.

While she loved reading and crafting at home Yuansui was a storm she couldn't resist.

``Er um. So you two really had a good relationship right?''

``To be honest being with her was annoying and bothersome. But after she fell sick that's when I realized how lonely it was without her.''

Haryeon grabbed onto Qing's hand.

And then with her lashes fluttering she speaks as if getting to the point.

``Sister, please don't hate the Emperor our father too much.''