\chapter{Legacy (2)}

``Uh, it's not like I hate him or anything.''

Hate or not I have some regrets about the Emperor well a bit but anyway. Whatever.

``When my older sister collapsed and all the physicians shook their heads and backed off the Empress… yeah she was out of her mind.''

It was a time when there was no joy within the Forbidden City.

Or at least there shouldn't have been.

The Empress's eyes were gleaming.

Just by looking at her smile it made me want to slap her hard—how dare she show such joy when the princess was in danger? How ungrateful can she be after all the good things Yuansui did for her?

All the palace maids fell silent sensing the atmosphere; the Empress's behavior was nothing short of a menace.

And Haryeon was no exception.

Your sister's collapsed and you're just lounging around? I'm not even asking you to change her bandages; can't you at least offer a prayer or join the rituals for her martial well-being?

How can a person be so heartless?

``Um. Well.''

It was a classic portrayal of a family collapsing due to a serious illness.

Losing a family member was a big deal but some losses hit even harder.

The concept of a ``good death'' exists for a reason; once you mentally prepare for goodbye and organize everything the pain doesn't sting as much even if you're saddened.

But unexpected losses especially the worst kind where you watch years of suffering drag everyone down into a pit—they weigh heavy.

``Honestly I wouldn't say I didn't blame my sister; it would be a lie. If only she had left sooner clinging to life just made it hard for her our mother me—everyone.''

``Hmm that makes sense…''

``And the Emperor too.''

The Emperor didn't show much reaction.

He called upon skilled physicians; when one left he'd send for another. In his eyes Yuansui's importance in the state affairs was like listening to a report once a month.

If that's how the Emperor felt how do you think the Empress was doing?

Your daughter was dying and you don't even flinch? Given he never liked her much it must have felt like a blessing. When was the last time he even looked at Yuansui's face? What's the use of being a father if you can't even help with that illness?

Yet the Emperor simply maintained silence and continued his daily duties…

``However the Empress couldn't sleep; I don't know how she felt but Mother had plenty of people to share her grief with. Father he didn't have anyone.''

Watching her father growing more gaunt by the day little Haryeon thought someone had to stand by him.

And she knew the way to comfort him too.

The warmth of someone who had barged into her chambers and collapsed there ``No can't we sleep in the room? I'm feeling sleepy don't talk to me'' yet in hindsight it was indeed a warm memory.

Seeing her young daughter hiding in her room the Emperor perhaps trapped in a corner couldn't bring himself to turn her away or maybe he didn't have the heart to refuse.

``He had put me on his bed and sat at the foot watching me. When he saw me sleeping so peacefully wouldn't he fall asleep soon too? But you know what? When he lay down he wouldn't stop talking. Maybe he needed someone to listen to even if someone couldn't understand him. I had no clue he was such a talkative person until then.''

``It's just like someone isn't it?'' Haryeon chuckles softly.

``Don't make such an apologetic face. Really sister I think it was fine even if it was fake. Mother softened and anyway the two of them always got along well enough; Mother's fiery personality probably met with Father's patience.''

``Hmm.''

``Since you don't remember I felt like I had to defend the Emperor. After hearing from Mother I thought that he would just remain someone who hated you.''

The hundreds of schools and thousands of teachers say that a king should work for the people.

He should love them be sympathetic care for and guide them with compassion.

But does a king really have to serve people?

If so how exactly should he do that?

The ruler of Zhongyuan was heaven and earth the world itself.

If the world serves people then who should it serve and whom should it neglect?

For one person to gain in life means another has to lose. If the heavens and earth were to move for an individual it would harm someone else.

Thus perhaps the world should be indifferent.

If heaven opens for one favored by it and the earth rises and falls for one it loves eventually the ground will crumble and the sky will break.

When that happens rivers of blood will flow drowning the world.

So heaven should remain vast in its place and the earth should simply sit below supporting what's beneath it.

That was how a king should care for the people and there's no room for favoritism.

This was the very reason why heaven's indifference benefits humanity which was its law.

Thus three thousand five hundred years of history have passed in Zhongyuan.

Sixty unified dynasties have existed yet only four lasted two hundred years.

There hasn't been a dynasty that lasted over three hundred years.

But if the current Zhu dynasty continues its reign the youths of today will soon celebrate the country's three hundredth anniversary in its long history.

``We were merely princesses to the Emperor. Even I one day will be offered as a gift to distant foreign barbarians fulfilling my duties as a bloodline of heaven. But I didn't want that so I went and plotted which isn't exactly my place to say. But I feel like I should stay in the palace.''

``Plotting?''

``That's a secret. But Sister, you're no longer Yuansui right? I think the Emperor might have been pleased. Of course I can't be sure how he feels… that's just what I think.''

And then Haryeon pulled the string to summon the palace maids subtly delivering her elegant departure request.

``It was when you received the title of Princess that you turned ten. The Emperor said he would weigh down your lighthearted demeanor with heavy responsibilities but how many times has a ruler who isn't even an adult had a princess raised in such a way?''

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's heart became even heavier.

Qing was soft-hearted in love and the Emperor's demeanor was bland and heartless which made her feel at ease.

But what if it wasn't like that?

An unfeeling Emperor who doesn't love the people.

To remain heaven earth must eliminate all who challenge its being causing innocent blood to flow every time the heavens shine and the earth shakes.

Yet thanks to this great wars that could result in the world's destruction were ultimately avoided.

In fact the country looks like a complete mess and if you go to any government office you find common people crying out in injustice.

Officials were corrupt and since it's not really a secret in Zhongyuan they openly engage in disgusting collusion while exchanging bribes.

Even if someone works hard if they lack luck and connections they go from rich to poor overnight. If they're lucky they'll just be poor and not a criminal which was like getting a mercy pass.

So everyone laughs at the honest as naive fools who don't know how to navigate the world.

Meanwhile martial artists—well the orthodox martial arts sects were a bit better but they're still private military groups just occupying territories and collecting protection fees.

Yet the nation keeps turning.

It's almost miraculous that it hasn't collapsed.

But it makes you wonder if there's really a reason to maintain one Central Plain one unified dynasty like this.

Is the land too big to manage?

Can't we just divide it?

Yet the obsession of Zhongyuan people for unity borders on madness.

After breaking apart it's always back to war war again.

And the wars in Zhongyuan were brutal.

Just look at how they treat captives; it's common sense to bury them in the ground.

After all whether they dig the earth or get buried in it covering them with dirt takes little effort so it's quite efficient.

It's a people that easily disregards the lives of millions.

Hmm.

If only there was someone truly bad to just hate and kill without a second thought.

The Emperor manages politics like a dog and who cares about ten years from now—just think about it then; life goes on.

But Qing's gut churns as she watches the indifferent expression on the Emperor's face.

It was the day of the audience again.

The previous audience was canceled due to the Emperor trying to grant too grand a reward of Princess Consort.

Then nearly headed straight to a dramatic conclusion with a noble wedding but the Emperor requested a simple refund of that decision and it fell flat.

Anyway ministers reluctantly cast their votes because it sounded like the Emperor was just trying to keep the martial world in check; truth be told they'd have preferred if he didn't bother at all.

And the Emperor's new proposal wasn't half bad either.

Finally the voice of heaven echoed.

"The young hero Ximen Qing is just a mere commoner. But the commoner drove off the enemies. This was a clear display of courage in fighting against those who seemed unbeatable all for the nation and its people. Thus heaven granted her miraculous achievements pushing back those foes. Honoring that I shall bestow the name on the young hero Ximen Qing."

A eunuch below the Emperor elegantly unfurled a scroll from his sleeve.

Written there were the characters ‘Tianhua.'

Hmm not particularly new.

In fact something novel could have been troublesome.

``Your grace I'm unbelievably grateful.''

But it wasn't over yet.

"Ximen Tianhua despises corruption and pursues justice showcasing the demeanor of a great hero. Moreover disregarding her own disadvantages also portrays the quality of a valiant warrior. Thus I shall have the young hero Ximen Qing serve the world."

Qing's eyebrows furrow at this.

It was a sign that an official position would be given.

That was the very position Chunfeng warned against taking at all costs.

\textit{Wait you promised ten years so why this position?}

\textit{Isn't this a different deal altogether?}

Then the Emperor continued declaring.

``I will confer the title of the Twelve Surveillance Inspector to Ximen Tianhua assigning her the duty of overseeing corruption in the nation.''

Twelve Surveillance Inspector?

Hmm what's that? Why is it only you who knows about it?

Inspectors plus officers does that mean a secret mission inspector?

Or something along those lines?

In any case Qing had been told never ever to accept such an official position.

So while trying to say thank you but feeling unworthy she took a deep breath.

``Your Majesty! No! I'm honored but please listen to my old voice!''

A loud voice suddenly interrupted.

Everyone turned their heads sharply.

There stood an old warrior dressed in general's attire and ready for battle ties secure fully prepared for a fight.

It was Qing kneeling and looking up at the Emperor.

Ummm was it okay for me to look back now or not?

I didn't learn how to handle situations when someone suddenly barges into the court…

But I'm so curious…

At that moment Qing found herself twisting to turn around.

Then a stunningly familiar voice rang out.

``Ximen Qing of the Martial World that girl was a treasonous rebel! I beseech you to allow me to immediately execute this horrific criminal!''

Before she knew it she was labeled a treasonous criminal and instinctively twisted her body to take a look.

And there she met a familiar face. 

\textit{What? Duke Fan Yue?}
