\chapter{Legacy (5)}

``Hey, don't take it the wrong way.''

Qing quickly steps back.

Right now provoking Duke Fan Yue would only endanger Qing himself.

First he needed to keep an ear open. To communicate one must at least listen.

This groundwork was crucial; speeches often begin with strong words to deliver a big shock so he starts off with some cheeky chatter to penetrate those ears.

The strategy in the art of war states that knowing oneself and one's enemy means you won't be in danger no matter how many times you fight.

If you know your enemy and yourself you'll avoid losing battles and if unavoidable you'll at least make efforts to minimize damage.

And Qing knew his enemy after narrowly escaping thirty-odd exchanges.

She understood Duke Fan Yue's level well now.

\textit{At this rate I might actually die…}

For now since she was starting to get used to Fan Yue's swordsmanship, Qing felt a bit more comfortable moving.

But that was all.

Fighting isn't a one-man show.

Duke Fan Yue would also become accustomed to Qing's movements.

Qing's body was beyond the capabilities of a normal human in every aspect enhanced with extreme flexibility obtained through brutal training. This allowed him to perform creative evasive maneuvers.

But what if the enemy got used to that?

They'd understand Qing's speed and reactions and the range of motion in his joints and even his tendencies—like which direction he preferred to move in certain situations and such.

Right now he might find things a little easier but that wouldn't last.

The skill of a warrior who has reached that level was nothing ordinary and catching up was just a matter of time.

So now Qing was counting on the Imperial Palace Warriors.

He couldn't do this alone. They had to attack as a group.

Lady but when on earth were you coming?

He had to buy time until then.

``Alright. I've painfully realized I can't face you so listen well. I'm only going to call you out once. Master Wuxianggong!''

``Wait—''

``All things in existence change and vanish in an instant like a flicker of the eye. Thus all that we perceive was ultimately impermanent so they claim it does not truly exist. Yet I Wuxianggong ask: Does true impermanence mean it doesn't exist? If it changes into something else has its essence itself changed? No its essence exists within change so if one can grasp the essence of all things one can understand even the mightiest changes.''

``Nice try but isn't that the impermanence doctrine of Buddhism? Wuxianggong Sutra isn't that kind of impermanence.''

``Ah.''

Qing flinched.

He thought he crafted a good argument at the beginning of his martial arts speech something brilliant that could work on anyone but that wasn't the impermanence he thought it was?

But the momentum was already there.

``No did I master Wuxianggong or did Duke Fan Yue master it? Wuxianggong might have been derived from Buddhist studies and I didn't ask him how to create it and don't you know that Buddhism and Daoism ultimately connect? Right the reign of all things!''

``Your face is the exact kind when you're trying to dodge the issue. I don't see a reason to discern its authenticity. You can just confirm it yourself—''

``Wait!''

Qing hastily waved her hands.

He had that desperate look of someone about to charge in.

It seemed the strategy of just calling any martial art like Wuxianggong for time wasn't going to work.

What the heck was happening? Do I just get automatically transferred if I die? Why was it so hard to kill someone without nonsensical dialogue?

So what to do?

As Qing desperately brainstormed suddenly one side of his head felt brilliantly illuminated.

``Look at this this!''

``Honestly if you just stayed still you'd avoid the pain—''

Duke Fan Yue's words were abruptly cut off.

Qing's hand was glowing with a brilliant light a dazzling indescribable multicolor glow he'd never seen before but intuitively it felt like a mystical substance from another realm one that impacted one's spirit and soul.

In Qing's hand emerged a square horn.

Just looking at it he could tell it was some kind of divine object of a spiritual nature; it felt like something interacting with not this world but another dimension entirely.

``You wanted Wuxianggong right?''

Qing presents the horn in his hand.

Of course it wasn't really Wuxianggong.

After enduring a long period of unconscious torture he'd rather choose death over this torment and his mind had crumbled. It was the Heavenly Demon Soul!

At long last Qing unveiled his ultimate technique after a long time the summoning of the Heavenly Demon!

``Alright I'll hand it over so step back I'm throwing it hard.''

``Perfect.''

Duke Fan Yue takes a step forward.

Qing stepped back in hesitations.

``Didn't I say step back?''

``Perfect! I wasn't feeling great about attacking the princess. If you want to live you better hand it over before you go!''

``Damn it agh ahhh!''

Boom! The sound shook Huanggu Hall.

But before that an old man's figure rushed right in front of him. What's this? It felt like the sound barrier had just been breached?

But Qing was already prepared from the moment Duke Fan Yue subtly lifted his feet.

The sword gliding close enough to Qing's face grazed him its fierce wind prickling his skin.

Qing's body was launched back barely escaping head separation crashing through the wall and out into the marble pavement outside.

Then came the shouts.

``There he is!'' ``Seize the traitor Fan!'' ``Hooray!!'' ``Long live! Long live! Long live!''

The voices pumping the morale echoed all around.

Simultaneously the shrill sound of a flute pierced the air alerting everyone to the enemy's presence.

As Qing rolled helplessly his back against the ground he could still see the soldiers rushing in through the chaotic scenery around him.

Those in golden clothing were the elite guards and those dressed differently with some makeup were the court eunuchs.

He never expected to be glad to see the elite guards and eunuchs!

And what's with that whistle sound?!

Qing quickly got up his face brightening as he dashed toward the Imperial Palace Warriors filling the vast courtyard of Huanggu Hall.

Boom the fierce energy crashed into him.

Yet Qing's figure split into eight.

It was Duke Fan Yue charging through tearing past the shadows scattering like mist.

Qing landed right behind a soldier in gold and immediately turned around.

The Imperial Palace Warriors each raised their blades sparkling with Sword Aura.

All of them charged directly at Duke Fan Yue the energy of the warriors tracing lines in the starlight.

And then it happened.

The Imperial Palace Warriors parted left and right.

Just like water flowing around a boulder they naturally separated.

But for the Imperial Palace Warriors it felt like a nightmare had just swept over them.

Suddenly an uncontrollable force of nature surged through and weapons stretched out stabbing comrades in their sides severing arms and even turning to cut through their master's thigh.

Those charging ahead began to slide blood spraying out as they went down.

Wow what was that?

Luckily I just dodged if I'd made a half-hearted counterattack I'd have actually been done for.

Because Duke Fan Yue's martial art wasn't designed to annihilate an enemy the force wasn't sharp allowing Qing to evade.

But look.

When the purpose was no longer to attack but to defend a force not for killing but for subduing; that's the kind of power when martial art was unleashed for its true nature.

``Defeat the traitor!'' ``Kill him!'' ``The Emperor commands!'' ``The Emperor's enemy!'' ``Die!!''

But despite this divine power the morale of the Imperial Palace Warriors remained fierce.

Their eyes bore a sinister red light swirling like a long tail clearly demonstrating that they weren't sane as they charged with abandon.

Duke Fan Yue's sword flowed with an indomitable grace.

A slow unhurried stroke but the force behind it was an immense river that no one could contend with.

People were soaring through the air blood spilling and suddenly one who jumped high crashed to the ground sliding while headless bodies took a few steps forward then collapsed.

Countless deaths.

Just an old man wielding a sword and yet those that dared to approach faced a brutal defeat like moths drawn to flames.

In an instant Qing could see the expression on Duke Fan Yue's face.

His round eyes filled with shock then softened as if grasping some conviction.

A shiver ran down Qing's back.

This old man had finally realized just how powerful his martial arts were and how to apply them to confront this situation.

But now it appeared he was beginning to comprehend.

Whatever it was that martial art must have been about firmly standing one's ground using the enemy's own strength against them.

Qing stomped down hard sending a jolt.

What would happen if this old man gained real experience in battle at his age?

Even disregarding that before he got any more accustomed Qing had to take him down quickly.

Plus what was going on with the elite guards?

They all ran at him without sparing their lives wearing gold attire.

All he saw were brutal squads ready for slaughter.

Of course he never had a good experience with the elite guards and they seemed willing to throw away their lives at the Emperor's command thinking the lives of commoners were mere tools to be discarded.

But still they did come to help.

He couldn't just let them die like that.

And most importantly—

They had to be killed now.

While they could still charge in like this when the elite guards could be recklessly rushing toward a master from another dimension now was the time to cut off their throat.

Ding!

The Buddha's Physical Body surged with the sound of a temple bell echoing through the air.

Duke Fan Yue's sword which had been flowing smoothly quivered subtly.

Although it's said that a sword can't cut water in that brief moment even water could split apart.

Ding! Ding! Ding!

With the ringing of the temple bell the dull blades of the elite guards began to shiver as if shaken off from some curse narrowly avoiding becoming part of a tragic mutual destruction.

And then finally the energy of the elite guards clashed against Duke Fan Yue's sword generating fierce sparks.

``Go! You lot!''

Qing ducks down snatching a sword from an elite guard who was still coughing up blood.

Springing up like a bowstring he lunges.

His sword pointed forward extends his elbow back as far as it could go and with his left hand he directs the blade at a target.

Boom! He strikes the ground forcefully.

The rebound from his stomp travels up through his ankle past his knee over his hip amplifying in a strange manner towards his sword.

He couldn't mimic the old man's grand stance.

After all he's a very well-off gentleman striking the ground like the center of the universe while the old Duke Fan Yue without any preparation casually thrusts forward piercing holes through the cliff face.

But I can't do that.

Duke Fan Yue strikes with a stylish flourish bringing his blade to the front and then slashing smoothly. Trying that would only leave me writhing in pain.

So I've got to do it my way.

I just need to muster all the strength I can and thrash about.

Qing's right arm shoots out like a beam of light.

A massive amount of energy from inside the Dantian relies on a final burst making all the energy meridians scream out in unison.

The sword he releases becomes a beam of sunshine bathed in golden light that pierces through the world.

Duke Fan Yue grits his teeth his jaw jutting out as he quickly swings distorting the arc he had drawn.

But that fierce light from Qing moving just a little faster grazes the shoulders and torso of the elite guard.

In an instant as if summoned by fate it darts toward Qing who has launched his attack.

Thud!!

With a thunderclap the beam thrust shoots off at a sharp angle.

That beam of light slams into the roof of Huanggu Hall—

Crash!! A massive explosion obliterates about a quarter of the ceiling sending dust skyward.

For a moment everyone stopped staring at Huanggu Hall with astonished eyes.

A section of that golden roof crumbled as if a boulder had fallen from the sky!

Then as if rehearsed countless gazes shifted toward Qing.

Qing opens his mouth to shout.

``How dare you! This traitorous scum! How dare you collapse Huanggu Hall! I won't forgive you!''