\chapter{Legacy (3)}

``Cheonhwa-geom is a rebel who daringly impersonated Princess Yuansui and claimed to be the rightful princess! She said Princess Yuansui of the palace says is a fake, while insisting she's the real one. How can there be such an absurd sin in the world!''

Qing's eyebrows twitched.

Did Yuansui's swordsmanship master suddenly have a reason to slander me?

Or perhaps he's plotting something on behalf of the Empress?

If it turns out I'm really of noble blood I might just have to remain in the palace as the princess.

Qing turned again to glance up the steps where the Emperor was seated.

The Emperor's expression was utterly bewildered, eyes wide and mouth agape in sheer disbelief.

And one step below, the faces of the Empress and the Crown Prince mirror that same shock.

An entire family comfortably shocked, how quaint.

As Qing observes the officials wear grim faces mulling over the serious accusation thrown by Grandmaster Gi-do-wi of Huanggu Hall.

The shameless claim that Ximen Qing dared to impersonate royalty was no small matter.

In Zhongyuan there's a major crime that gets executed without question— impersonating a prince was certainly among the worst.

But.

``Gi-do-wi what do you mean? Impersonation? What exactly does Ximen Cheonhwa stand to gain from pretending to be a princess?''

With a voice that feigns calm but trembles slightly the Empress inquires.

The officials shared her sentiment.

Why out of nowhere? Besides didn't Ximen Qing already hear the news about her being designated the Crown Princess?

Without any notion of the Crown Prince's intention to imprison her she must have believed she would enjoy great wealth and power as the future consort.

Why on earth would Qing bother to impersonate a princess?

``I—I have no idea what sinister plan this treacherous rebel concocts! But given the crime of impersonation am I not justified in accusing her for claiming herself as Yuansui?''

Qing was flabbergasted.

\textit{When did I ever—}

``You've openly told the palace maids in the healing room that you would have them pull Yuansui down and take her fraudulent place to enjoy wealth and power!''

All eyes were on Qing now the officials waiting for a response.

Qing was left speechless.

There's so much to say.

\textit{Did I say that? No, you said it! I told you I'm not Yuansui! But you insisted I was and now you come at me with this.}

\textit{And what's with the healing room maids nonsense?}

\textit{I never breathed a word to them!}

\textit{Still there's a high stake in arguing right now.}

\textit{Should I to say I'm the real one?}

Master Beom-yak was in a rush.

If Yuansui becomes the Crown Princess confined just like that he'll sit back and wait for an opportunity to reclaim the Divine Skill.

He figured since she learned her lesson she'd hang herself in despair.

As much as he reached harmony how hard can it be for a martial arts master to handle a petty dispute?

Let Yuansui be who she is.

Her original role was to guard the princess after all; by saying she couldn't distinguish the fake from the real he could merely request a demotion then return to guarding Yuansui and reclaim the Divine Skill later.

In either case Yuansui would remain in the palace so Beom-yak had no rush.

But.

Lightning could strike in a clear sky indeed.

As the Grandmaster Gi-do-wi of Huanggu Hall Beom-yak observed the scene unfolding from above.

They want to appoint Ximen Qing as an official examiner?

Examiners usually oversee designated regions but the role of a Grand Examiner spans the entire Zhongyuan.

Though a lowly sixth-rank official its authority was immense; the results were sent directly to the Emperor bypassing other channels.

Yet due to its travelling nature once appointed it's nearly impossible to return to the Forbidden City.

For someone like Beom-yak tied down in Huanggu Hall this news felt like a clap of thunder.

Let Yuansui go just like that?

While there's a small chance to return he wonders how much time he truly has left.

A master may regain youth through Reverse Flow and Return to Youth but it doesn't grant them eternal life.

No matter how long a person lives limitations will eventually find them.

The reclaimed youth faces rapid decline once it hits the limit signaling one to prepare for the end.

Beom-yak's condition was just that.

At one hundred and three years old his once youthful vigor quickly faded and with each tired awakening his body felt heavier.

So the choice presents itself.

Accept that having lived beyond a hundred was a good enough life or push through the walls of fate a little longer.

Typically masters in the martial world know when to accept their limitations.

Upon reaching the celestial realm they realize their boundaries and how arduous the future steps will be.

At the moment when a warrior who has lived a life of struggle yields to the heavens' order that's the moment of resignation.

But what if there's another way?

If only there's a means to reach the next level one that seems achievable with my talent and ability.

Beom-yak's empty tome the storage for the contents of the Divine Skill was that very answer.

And now a voice reaches out to him like a persistent melody.

``Duke Yan, there seems to be a misunderstanding. Ximen Tianhua is indeed a true descendant of the Divibe Blood, the real Yuansui! How could revealing her true nobility be a fault? It's merely the Heaven wishing to set her free.''

It was the voice of the Crown Prince's guard the Silent Gi-do-wi.

``But it's only natural for the gasping Grandmaster Gi-do-wi to rage over such words; His Majesty will show mercy so please withdraw for now.''

The Silent Gi-do-wi cannot independently deliver this message; it carries the Emperor's intent.

'Don't create more fuss and step back; I understand your feelings so let's treat this as if it never happened.'

Beom-yak mutters under his breath.

Ah 'don't miss a good opportunity.'

'Don't lose this chance' it means.

And until now Beom-yak had been afforded numerous opportunities.

As someone who could roam the Imperial Palace at will if he had studied the tomes for enlightenment…

He could've gotten his hands on the Secret Manual before Yuansui.

But he hadn't.

He thought his achievements were enough so he didn't bother hunting for any other skills to practice.

And now?

If only he had seized the chance when Yuansui strolled into the palace disregarding everyone's gaze and directly reclaimed the Divine Skill.

Beom-yak gently closes his eyes.

If I let this chance slip away when will it come again?

Even if I wait for an opportunity to arise how much longer will this frail body last?

Beom-yak collapses to his knees.

Yet his mind remains crystalline clear.

If he draw his sword now, the Emperor's guard must protect His Majesty which means he have no need to deal with the likes of the Crown Prince's guards.

So taking down one girl from the Realm of Transformation should be simple enough.

Of course afterward he'd find himself pursued as a great rebel by the armies of Zhongyuan.

In Qing's hometown there's a joke:

'Borrow as much money as you can from every place, then go buy a tank.'

'What? How will I pay it back?'

'Pay it back? You'll have a tank by then!'

\textit{Once I obtain the Divine Skill and rise to Zhongyuan who could stop a great martial artist like me?}

\textit{Even if I don't reach the next level, my life is limited as it is, so it's my fault for missing the earlier opportunity—what harm can come?}

\textit{If I had known this would happen I would've steeled my resolve earlier.}

Thunk the sound of kneeling.

``Your Majesty, I only seek to serve you with utmost loyalty!''

The Emperor's stern face softened slightly in response.

However Qing's eyes narrowed.

Beom-yak draws his sword.

One may question how brazen it was to draw a sword in front of the Emperor but the lead guard has to be armed during the Emperor's court.

And Qing seeing a sword drawn by a kneeling man never lets her guard down.

Far from relaxing an even greater vigilance wells up.

For Qing, kneeling wasn't about begging for mercy.

Kneeling was an infamous tactic of endurance employed by the great general Han Xin known for his unparalleled cunning—he endured humiliation to strategize for the future.

Thus kneeling was a maneuver to gain momentum no doubt.

\textit{Moreover this old man pretended to be all nice and friendly to me until now.}

\textit{Now he's pulling this?}

\textit{Suspicious, very suspicious.}

Suddenly Fan Yue's posture wavered.

It's hard to put into words but it seems like his figure vibrates shifting left and right fading like a mirage.

In an instant the old man's sharp gaze forms a straight line right in front of Qing.

Simultaneously Qing's form split.

She dispersed in eight directions, soaring twirling a flurry of movement.

The sound of a blade slicing through the air fills the space.

Beom-yak's arm was fully stretched as Qing spins like a top landing softly despite the rotation.

But Beom-yak turns leaving behind a mere afterimage as he vanishes a beat too late.

This was the legendary move of ``a single figure becomes two'' allowing one to narrow the distance using the arts of ethereal movement.

Originally the ability of Nengpa Mibo forces one to maintain an unfavorable position against a master.

Why was this old man speeding up so suddenly?—Ouch.

Qing collapsed hitting the ground.

Though she couldn't see behind her back she sensed someone lurking.

``Jungpil! Fetch the Crown Prince!''

The Silent Gi-do-wi barks seizing the Emperor and simultaneously grabbing the Empress to secure her by his sides shouting.

The guard referred to as Jungpil quickly drops from the ceiling and lifts up his master.

``Subdue Grandmaster Gi-do-wi! You have permission to take action!''

The Emperor's command resounds.

At this the Empress snaps back to attention.

``Let go let go! Yuansui—''

``Forgive my rudeness!''

``Wait! No let Yuansui—''

The Empress's screams fade softly into the distance.

The guards' sole mission under the heavens was to preserve the Emperor's body.

A master daring to strike at the princess in front of the Emperor must be swiftly escorted to safety.

So when Qing suddenly rises chasing an opponent that flew past her the steps were already empty.

Wait they're fleeing already? So soon!?

But it works out better this way.

If I can slip out now all the better.

If not I can always run later.

Qing reflects as she steps back into position aware the royals have personal guards while the officials still can't grasp the situation; she targets an unfamiliar nobleman with the supernatural ability of Nengpa Mibo initiating it.

One of Qing's eight divided figures lands back regaining original color and securing a foothold beside a pillar.

And with a loud crash she propels herself the floor of Huanggu Hall splitting and releasing black mist-like True Energy.

One step, two steps.

Three steps to maximum speed.

Qing rushes toward the Forbidden City courtyard.

Just behind her a sweet sound caresses her ears.

The sound of steel slicing through flesh.