\chapter{Legacy (6)}

Behind any great feat that seems impossible for a mortal to accomplish, there was always a lingering aftertaste.

The move that Qing demonstrated was a truly thrilling destruction, and the reason all eyes were on him was likely to show reverence for that magnificent blow.

However,

``How dare you defile the Huanggeon! The glorious cradle of history, which has held a thousand years of time!''

It was a remark that shattered respect in a single blow.

Moreover, where did this thousand-year history come from? The Forbidden City has only been around for about two hundred years, so by the standards of Zhongyuan, it was still considered a new construction.

``Why do you try to shift the blame onto me? If I had not deflected it and had instead struck it, it would have collapsed under its own weight, wouldn't it?! And a thousand years! The Forbidden City was barely two hundred years old!''

The voice was full of sincere grievance.

But Qing would not back down and retorted boldly.

``Who was responsible for guarding the Huanggeon? Whoever broke it, if they couldn't stop such a brutal destruction, then it was the fault of the one in charge of the defense! And two hundred years, you say? The spirit of Zhonghua's thousand-year legacy resides there! How dare you belittle the Emperor's great hall, you barbarian! No, you are the barbarian itself!''

``Wha-''

Duke Fan Yue flinched.

It made sense because if a thief broke into a house, it would be the fault of the guards.

``How dare you reduce Zhonghua's thousand-years history to just a thousand years! A thousand years ago, before the Great Tang Dynasty, countless ancestors—''

``Ancestors? How dare a traitor mention the ancestors? How dare you, the despicable traitor who attempted to assassinate the Emperor, speak of ancestors!''

``What do you mean, assassinate the Emperor? Who—''

``Shut up! The Captain of the Huanggeon's guards, under the cover of night when no one was around, dared to invade the Emperor's royal office and sit in it! You old man must have been plotting rebellion all along!''

With every word, baseless slander poured out.

From destroying the Imperial Palace to being a barbarian, and now being accused of dreaming of murdering the Emperor—each false accusation naturally followed the other, all intended to smear him.

However, instead of defending himself, Duke Fan Yue widened his eyes in shock and gave a stunned expression.

``Oing? What? Did you really sit in the Emperor's office?''

``No! How dare anyone covet the Emperor's office—''

``Wow, he really is a traitor! Look, everyone, listen to what this old man is saying! He was supposed to guard the Emperor's office, but instead, he sat in it, proclaiming himself the Emperor! Ha ha!''

All eyes turned to Duke Fan Yue.

'Really? Did he really sit in the Emperor's office in the middle of the night?'

Duke Fan Yue's face turned crimson.

Whether it was due to shame or grievance, only he knew, but his refusal to respond and his tightly closed lips suggested it was more the latter.

This was the power of a venomous tongue, sharp as a deadly viper, able to strike with lethal force.

Qing, who had no regard for authority or face, was always straightforward and bold, preferring to be seen as a comical, approachable figure rather than one to be feared or revered.

Therefore, Qing was an extremely wicked woman.

She was naturally the type who would not lose by being seen as a ridiculous woman to others.

In contrast, those in Zhongyuan, particularly the elderly or those with high status, held their dignity and face as precious as life itself.

To drag someone into the mud with no benefit, just to force them to lose face—that was a wickedly cruel scheme!

Yet, we, the three-in-one entity, our descent into hell together was a remarkable feat in itself.

``How dare you insult the Emperor with such disrespect! I, Qing, the young hero of justice, will not forgive you in the name of righteousness!''

Boom! Qing stomped on the floor and charged forward.

The booming sound of her footsteps shook the surrounding Imperial guards, who had been watching the argument in stunned silence, snapping them out of their stupor and immediately launching into action.

But since more guards were already gathering, a great number of them joined in during the brief exchange.

Duke Fan Yue's sword swung in circles.

It shed countless blades, but unlike before, it didn't return the favor with sharp counterattacks, and the intense fighting spirit had disappeared.

That was because Qing was coming at him.

The sword drawing in circles now moved for basic self-defense, but inside, it was charging energy for the ultimate moment when the conflict would reach its peak.

The critical moment where Huang Taeguk's power would be unleashed on the world!

The final chance to recover from this dangerous situation—escape with a victory.

In that moment, Duke Fan Yue's eyebrows twitched.

\textit{Why is Yuansui charging at me?}

\textit{Although she might feel pity for the Imperial guards who were dying, did she truly believe charging recklessly would help in the face of that overwhelming power?}

Duke Fan Yue's eyes hardened with anger.

The moment Qing, in a desperate move, extended her sword…

It split into several phantom images, extending in all directions.

A stunning display of splitting techniques, creating illusions that confused the opponent.

In that instant, Duke Fan Yue's eyes flashed.

The eight divisions were illusions meant to deceive, but ultimately, they were just a flawed technique that exposed its weaknesses.

When Qing, semi-transparent, landed on the ground, Duke Fan Yue's movements scattered, and he soared through the air to strike at her from above.

With a sharp, flashing sword strike, Duke Fan Yue's blade aimed directly at Qing's head, moving downward in a lethal arc.

Crack!

The sword struck her skull.

It pierced through, slicing downward as Duke Fan Yue's blade struck with overwhelming force, only for the attack to miss!

The divided Qing disappeared, leaving behind a hollow chase for the illusion.

``Take this!''

Qing shouted as she leapt to the right, extending her left arm in an elegant arc.

Her sword came back to life with a bold, forceful thrust.

Duke Fan Yue hurriedly turned, lifting his sword with one hand to block, charging his energy for a counterattack.

But at that precise moment, Qing thrust her sword forward again, this time aiming for the air itself.

The attack missed, leaving only emptiness in its wake.

It was nothing but a bluff, pretending to throw the sword.

Qing, with his unique skill, used a modified thrust not to jab, but to throw the sword itself, reducing the recoil.

However, since he released over three-tenths of his inner energy in a single instant, the shock of that force was impossible to mitigate, even though he was already in the realm of transcendence.

Of course, he could have fired even more.

But why?

To make the core feel the fear, delivering a single blow was the best method. Once that fear was instilled, it's enough to threaten them with the core next time.

But instead, there was a *ding*!

The sound of the Buddha's bell rang as Duke Fan Yue's head jerked back, his gaze quickly filling with rage as it locked onto Qing.

But that moment passed quickly.

``Die!'' ``You traitor!''

Qing wasn't alone, though.

After always fighting against the odds, it felt incredibly reassuring to finally be on the side with the numbers.

Ah, so this was what it's like to fight with support.

Duke Fan Yue's sword again traced a soft circle, claiming all the space around him.

However, unlike before, there was no intense burst of blood.

Unlike the Royal Guards with their glowing red eyes, the Imperial Eunuchs moved in flawless harmony, as if performing a delicate and precise art.

Three or four of them simultaneously rushed in, some supporting from behind to increase the speed, others pulling back dangerous foes while coordinating attacks from every angle—left and right, front and back—free to advance or retreat at will.

The sound of steel clashing repeatedly echoed.

At some point, the bright-eyed Royal Guards replaced the red-eyed ones, and the new arrivals moved with a clear difference in their agility—these were true masters of the craft.

Qing, adjusting her position, pulled back her elbow.

She aimed her sword, pretending to throw it, but Duke Fan Yue, already struggling to control his body, kept glancing at Qing, looking for a way to counter.

``Hyah!''

Qing released her sword with only a fierce momentum behind the swing.

Duke Fan Yue flinched, his body shaking.

In that instant, a blade sliced across his back.

His old body wavered, but a flash of inner energy surged as he attempted to recover, refusing to lose this opportunity.

``Hyah! Die!''

Qing shouted, again thrusting her sword.

Duke Fan Yue's heart sank. If that hit him, there would be no surviving!

In desperation, Duke Fan Yue hurled himself forward.

But all that awaited him were the kicks from the Imperial Guards and the blades of the swords.

Three consecutive bluffing strikes.

``Arrgh!''

That moment arrived.

A beam of light shot towards Duke Fan Yue.

*Clang!* With a massive crash, Duke Fan Yue's form shook violently.

Qing blinked. 

\textit{What was that? Who shot?}

Her gaze darted around.

Up on the wall, a heavily armored guard had appeared.

In his hands was a massive bow, and from his back jutted a vicious-looking arrow, akin to a throwing spear.

Soon, other guards dressed in the same attire leaped into position, pulling their bows to aim at Qing's side.

\textit{Ah, so they have archery techniques too.}

\textit{Well, of course. It makes sense. There's no reason not to have them…}

The reason there weren't any archers in Wulin was because the government had absolutely forbidden any archery techniques.

Before the reign of the Heavenly Emperor, the imperial authorities had suppressed all archery techniques, eliminating them from the mainstream. Even now, archery didn't hold a dominant position in martial arts.

So why did the government suppress archery?

Qing realized the answer clearly.

Because they wanted to keep it for themselves…

The Royal Guards, the Imperial Eunuchs, and the archers who had set up on both sides of the walls—Qing no longer even needed to bluff with his sword.

Even if they were masters of the current realm, the number of martial artists in the area was already considerable.

Additionally, while Qing had to keep watch for Duke Fan Yue's sword strikes, arrows with inner force were now flying at him, disrupting his flow.

It was clear that his strength was waning, and with each passing moment, iron arrows began embedding into Duke Fan Yue's old body, adding painful adornments to his wounds.

At this point, Qing didn't even need to step in. The end for Duke Fan Yue was nearing.

And then, it happened.

``Arrgh!''

Duke Fan Yue's form closed in on Qing.

Was there still enough strength left to break through the encirclement?

What kind of monster was this man, with such willpower?

Qing watched as Duke Fan Yue charged toward him.

His eyes were shriveled, with veins popping from his sclera, and his teeth were bared in a ferocious snarl—a face full of hatred.

In Duke Fan Yue's eyes, Qing reflected.

Once more, he pulled his sword back, preparing for a devastating throw, his cold, calculating eyes locked on Qing's face, the face of a perfect beauty.

Qing's sword technique shot forward.

A dazzling blaze of golden energy erupted, the sword now resembling a club more than a blade, radiating fiercely as it moved.

Duke Fan Yue's sword, too, began to shine with starlight.

It was his final strike, pouring all of his remaining strength into it—a final, desperate blow, meant to tear through Qing.

And then, at the moment of impact—

Qing's form scattered into eight illusions.

Duke Fan Yue's sword cleaved through empty air, helplessly slashing at nothing.

And as the illusions faded, the Imperial Guards passed by, swiftly delivering the final judgment upon the traitor.

Because Qing hadn't wanted to join in, but this was a battle of no choice.

\textit{What reason did I have to die so violently? An old man driven to madness, attacking with everything he had, as though with nothing left to lose.}

Qing turned her back.

Numbers always mattered, but there, in front of him, was the dying Duke Fan Yue—stumbling, bloodied, and unable to defend himself any longer.

Finally, the ground!

Duke Fan Yue's sword broke and flew off.

With a sharp whistle, the Imperial Guards retreated as their formation shifted.

Duke Fan Yue was left a tragic sight.

His back, shoulders, and arms were embedded with large iron arrows, his clothes torn to tatters, soaked in blood that streamed from his wounds.

Breathing heavily, his breaths came in ragged gasps.