\chapter{Legacy (8)}

Qing couldn't help but recall the image of Asiya, who had been in charge of the event at the Heavenly Maiden Temple, or perhaps more accurately, at the villain's rehabilitation gathering.

The sinister incantations that echoed throughout the event, the dance-like movements of the short daggers that seemed almost divine.

It looked as though she was carelessly scratching at something, but in reality, her skill was so refined that the blood didn't spill from the small vessels to the larger ones, as if she was a seasoned butcher performing the ritual with deadly precision.

If it hadn't been a situation where a beast was being slaughtered in the guise of a human, Qing might have immediately drawn a sword and declared the sorcery unforgivable. But Asiya, as the leader of her faction, exuded an imposing aura that demanded respect.

Qing had thought about inquiring about the resurrection ritual, but since the imperial family had decided to consider the matter as if it never happened, it seemed a pointless pursuit.

It was clear that the imperial family realized they needed her.

Hmm, let's take a closer look at the person.

If she didn't seem like an enemy and was genuinely just curious, it would be fine.

But even if the matter was brushed aside, confessing that there had been a problem with the ritual would be a completely different matter. Would she be willing to answer honestly?

Qing stood in front of the door, lost in thought.

The moment the door creaked open, Asiya's bare scalp came into view, clearly visible at the bottom of the doorframe.

Her body was pressed firmly against the dirty floor (as in Zhongyuan, people wore shoes inside the house), legs spread at a right angle.

Her body, from the tips of her toes to her knees, pelvis, chest, forehead, elbows, and the back of her hands, was completely and firmly pressed to the ground—an exemplary display of the five-body prostration.

Then, with remarkable skill, she wriggled her body, crawled up to Qing's shoes, kissed the toes, and wrapped her arms around her ankles, crying out:

``I'm so sorry! I've committed an unforgivable sin!''

What started as a submissive answer quickly devolved into a pathetic and groveling plea from the very first moment.

``Please, Your Majesty, I beg of you, show mercy just this once. I am the Heavenly Maiden, this lowly woman will explain everything to you, okay? Please, please, have mercy…''

Hmm, this voice sounds about right.

Asiya rubbed her cheek against Qing's shoe as if she were trying to polish it, begging.

Unfortunately, shoes in Zhongyuan were not made of polishable material, so it couldn't serve as a new technique for polishing cheeks. But it could be verified as a new technique for cheek rubbing.

``Hmm.''

Qing chose to remain silent for now.

Asiya was already in a submissive position, physically pressed to the floor, and Qing found it amusing to leave her like this for a while.

Yes, it was strangely amusing.

If asked to lick, would she really do it?

``Do you know about the Koryo bowing ritual? It's what the Koryo people use when apologizing. They press their forearms to the floor, straighten their bodies, and stand on their hands in an inverted position—''

``I'm sorry!''

``Oh.''

Qing clapped her hands with approval.

Asiya understood the hint right away.

``Alright, calm down. I didn't come here to scold you.''

Then, Asiya collapsed back to the floor, crawling like an insect, wrapping her arms around Qing's ankles.

``Then, my siblings… Your Majesty, I'm a sinner. Please, instead of punishing me, release my siblings. I won't even ask for anything else, not even to serve as a palace servant. I beg you, I'll serve you in any way you desire, just spare their lives…''

``Huh? Siblings?''

``They were poor children. In the land where they were born and raised, they were oppressed, despised, treated worse than livestock. But now, they're starting to smile again, Your Majesty, please. I'll tell you everything…!''

``Calm down for a moment.''

``No, I'll accept the punishment! This lowly woman cannot stand such transgressions, but my siblings, they did their best! For forty-nine days, they tried to keep Your Majesty alive, working tirelessly and passing out time and time again. They deserve mercy! Punish me if you must, but they've done their best!''

It seemed she wasn't willing to offer her neck, likely because she didn't want to die. But still, without arms and legs, life would be miserable, wouldn't it?

``No, calm down, alright? Why were you pulling at your skirt?''

``Please, Your Majesty, we've done our best. The reason you're standing here today, so strong, like the sun, was because of the little help we gave you. So, if you think about it, we're the ones who saved you, and I'm sorry for what we did wrong, but we were deceived as well…''

``No, calm down. I'm not here to blame you.''

At that, Asiya's eyes brightened.

With her posture, she twisted her neck in a way that seemed to strain her spine, but she looked at Qing with desperate eyes.

``Then, my siblings…''

``Huh? Why were you still talking about your siblings?''

``Ah, Your Majesty, please! I'll do anything, anything at all, just spare them!''

She quickly reverted to her previous posture.

After some coaxing and reassurance, Qing finally heard Asiya's troubles.

The imperial family had decided to pretend nothing had happened with the resurrection ritual, which was a solution typical of the Zhongyuan people. However, the audacity of swapping out the princess was something that could not be overlooked.

About half of the Heavenly Maiden Temple's yogic practitioners had been dragged away by a group of armed men. They were being hauled off, their heads grabbed roughly, and they were destined to be thrown into the infamous prison of the Eastern Palace, waiting for their inevitable deaths.

``If you spare my siblings, Your Majesty, I will serve you with all my heart…''

``Hm. Let's wait a bit. It's not really a time for talking right now.''

So, Qing decided to leave for the moment.

However, it was still a difficult situation.

Qing had no business intervening in the imperial family's affairs.

Since she was no longer officially a princess, the so-called ‘resurrection technique' was nothing more than a sham, and Qing was just a simple wandering swordswoman now.

She had no intention of pretending to be a princess anymore.

Besides, she didn't have any influence over the imperial family.

If there was someone she could contact, it would be the Empress, but even that seemed like a long shot.

Whoever heard this might think that the Empress had some strong connection, but in reality, it was just a thin thread, a mere acquaintance.

The Empress only smiled softly in response.

``Yes, my daughter. Remember this. To tame a person, you must show them kindness, not intimidation. Even those lowly, despicable women—once they have received a favor from you, they can't help but be of use to you.''

``Yes, Mother.''

``Still, it might be better to wait a bit. At least, putting the neck in the executioner's block will make those who have barely escaped death understand what mercy truly means.''

In other words, Qing had deliberately put Asiya in this position, knowing she would come looking for him, so he could bestow mercy. He had intentionally trapped her in a situation where she could feel the full weight of that mercy.

And mercy, after all, was felt most strongly when it follows a close brush with death. So, Qing had planned to let her briefly experience the executioner's block before saving her.

Hmm, the Empress's love was both heavy and terrifying.

Back to the Heavenly Maiden Temple.

This time, when the door opened, the view was filled with heads—numerous of them, packed tightly together.

It was the full assembly of the Heavenly Maiden Temple's yogic practitioners.

However, instead of crawling on the floor in the embarrassing five-body prostration, they sat politely, bowing deeply in a proper display of respect.

Having crawled over to kiss the shoes and rub their cheeks against them, there was no way to undo the initial impression of groveling, even if they tried to act dignified now.

``Your Majesty, this grace, I am eternally grateful.''

``Eternally grateful indeed.''

``Well, no need to go that far.''

``No, Your Majesty, locked in Dongchang's prison, the poor children thought they would never see sunlight again. Now, having been released so suddenly, they will carry this grace with them for the rest of their lives.''

Qing's worn-out triangular-shaped conscience—the one that had nearly turned into a circle—was spinning in circles.

Hmm, she doesn't know what she's doing, right?

Still, it wasn't something to feel terribly guilty about.

The Empress might say that the treatment was harsh.

After all, Qing had pushed them into a life-and-death situation just so he could bestow mercy.

Indeed, the monks' cheeks were pale, their eyes dull, their faces showing the signs of having nearly died and returned.

But they weren't exactly innocent either.

The monks of the Heavenly Maiden Temple had performed the resurrection ritual, and when it failed, they had hidden the bodies and found substitutes to perform a false ritual.

When one thinks of the mother who had to welcome a fake ritual without knowing her own daughter was dead, even if Qing had actually used an executioner's block, there would be no complaints.

And furthermore, the Emperor, too, had used the opportunity to execute a criminal.

They would cut whoever was handed to them. They wouldn't distinguish between good and evil.

``The resurrection ritual?''

``Yes, the soul transfer? In the Zhongyuan language, it's akin to the mind. In Zhongyuan, people believe that when a person dies, their soul enters a closed realm—unable to escape the three thousand worlds. However, in reality, once the soul was freed from the body, it was reborn in a world with the same height in the three thousand realms.''

Asiya spoke confidently.

She had successfully performed the soul transfer ritual before in the land of Tianzhu, though it had caused the death of her own shaman, who was hunted for practicing the evil sorcery. But still, the ritual had been successful.

Yet, the resurrection had failed.

Qing hadn't expected this, but when she thought about it, perhaps Zhongyuan people went to a different place than the Tianzhu people.

``Oh, I see.''

``Well, in the end, we succeeded in bringing Your Majesty back, so perhaps we can say it worked. We saved you, so I may have said something a little shameful earlier… Should I kneel?''

Is this woman an actual fraud?

Listening to the Empress's words, Qing thought it sounded like a wicked cult, but now, seeing Asiya as the leader, she seemed more like an incompetent fool pretending to be sophisticated.

Qing suddenly understood the Emperor's decision.

Even though they had committed the grave sin of swapping the princess, they had decided to bury the matter.

Of course, it was embarrassing to say aloud.

There was also the fact that the Empress was involved in the production of the new Imperial Guards, so there was still a practical use for the Heavenly Maiden Temple. But more fundamentally, they were harmless.

They didn't pose any real danger, and they begged for their lives, so they were useful as long as they were kept alive.

Perhaps this was Asiya's survival strategy.

No one would be suspicious of someone acting like a fool.

She must have been pretending to be clueless all along.

Otherwise, how could she have kept the fake resurrection ritual going for so long without it being exposed?

Maybe she was also using her younger siblings as hostages, claiming they were being held by the imperial family.

But now, what was the point in investigating Asiya's true intentions?

There was no reason to continue examining her now, after all.

``Is it possible for another soul to enter during the resurrection ritual?''

At first glance, it seemed similar to a ritual used to create a poison that transformed the soul, but…

Cultures differ, and so do the sorceries.

Magic, after all, was rooted in the realm of language, and if enough people believe in it, it becomes reality—faith-based outcomes.

Thus, the rituals involving soul transfers and the so-called ``soul-binding'' would seem similar but were not the same.

``Your Majesty, we were not begging the spirit to return. We simply pull the mental chain that binds the spirit to the body. The spirit wouldn't want to go to such a terrible prison.''

In Tianzhu's tradition, the body was a prison for the soul.

All souls long to escape the body and find freedom, but the laws of the world prevent them from doing so, forcing them back into another body.

However, based on karma, those who have accumulated evil deeds in their past lives were bound to miserable bodies, while those with good karma were reborn into noble bodies.

Thus, the soul transfer ritual was an evil one.

It drags the soul, which has already been freed from the prison of the body, back into it by pulling the still-attached chains.

So no other soul can enter.

Once the chain binding the body was pulled, how could another soul be dragged in?

If you pull on the leash of a dog, only that dog comes; no random dog will appear wearing the leash.

``Ah, I'm sorry! I didn't mean to say ‘dog'!''

Gabiya immediately flips onto her hands.

There's no such thing as the Koryo apology bow in the Koryo Kingdom.

But regardless, Qing wasn't in the mood to watch that display.

Could another soul really enter?

Then what about me? What am I, exactly?
