\chapter{Legacy (7)}

*Beep beep bee-*

With the sound of a whistle, the Imperial Palace guards began to withdraw in unison.

To be precise, they stepped back ten paces from Duke Fan Yue, forming a circular encirclement.

Qing glanced around.

Even on the roof of the almost demolished Huanggeon, and beyond the walls of the plaza, dozens of guards wearing glossy black silk robes and armed with bows were drawing their strings and aiming with deadly precision.

The true power of the Bureau that the Emperor had referred to as the ``martial artist'' might very well lie with them.

Though it was said to be fifty-strong, which might seem small, in reality, it was an intimidating force.

From such a distance, to be able to cut through a fierce battlefield and accurately project their energy as sharpshooters, it wasn't something you could easily estimate.

Perhaps there were even more special forces standing by—maybe artillery or other hidden troops?

The elite snipers in black looked towards Duke Fan Yue.

But the Imperial Palace guards, having formed the encirclement, were staring intently at Qing.

\textit{Hmm. This is it, isn't it?}

Qing took a step closer to Duke Fan Yue.

Another step, then another.

No one stopped her, and so Qing came to a firm conclusion in her mind.

\textit{Yeah. They want me to kill him.}

\textit{But it's a bit too crowded for me to enjoy this…}

Duke Fan Yue kept his gaze fixed on the ground.

The sound of footsteps echoed in the Huanggeon Plaza, a crisp and rhythmic sound that resonated through the air.

The ground of the Huanggeon Plaza was designed with seven layers of stones, each carefully stacked to produce a lively sound when walked upon.

It was an almost paranoid measure against potential assassins—no matter how much one tried to muffle their steps, the seven layers of green stones would inevitably produce a noise.

And if the captain of the Imperial Guard had reached the level of a current martial expert, no one would be able to approach the plaza unnoticed.

But what was the use of such architecture when the captain himself was a traitor?

At the sound of footsteps approaching, the traitor raised his head.

``That sword style… my hands still feel numb. What was that throwing technique?''

Qing raised her guard.

\textit{What's this? A stalling tactic?}

But only for a moment.

As a physician, Qing could already tell that Duke Fan Yue was nothing more than a walking corpse at this point—more a cadaver than a living being. This was close to a final lamentation, an expression of someone at death's door.

``It's the legacy of Celestial Martial Emperor. Solitary Nine Swords, Second Movement: No Malice, No Hero.''

``If it's not vicious, then it's not a true blade. That doesn't suit your style.''

``It wasn't meant to be throwing, but thrusting, and it wasn't meant as a surprise attack. At least, the Celestial Martial Emperor intended it to be like that. It could've been executed lightly, like extending chopsticks.''

``Ah, I see.''

When Wutian Great Master perfected his sword, he was already beyond the number one martial artist in the world, having reached the level of the greatest martial artist in history. Would such a transcendent figure need to resort to petty surprise attacks?

Thus, even the unmatched blade must wield a ruthless edge.

The true style was not one of dominance, but of subjugation—standing atop the heavens, above all else. Between the heavens and earth, humans must be ruthless, for humans were cruel beings.

This was the ideal martial artist in Wutian's eyes.

``That's right. I should have been more ruthless.''

``More so than now?''

Duke Fan Yue's expression twisted.

It was a smile, but not quite—a self-deprecating smirk.

``I was not ruthless enough. The Great Master once said, ‘If one gains the Dao in the morning, one may die by evening.' I should have killed you and fled long ago. Had I ended your suffering earlier, it wouldn't have come to this. I was not ruthless enough.''

He was speaking of the pain from the failed resurrection ritual.

For some reason, this old man had convinced himself that by killing Princess Yuansui, he would be able to acquire the wisdom he sought. He likely thought that Yuansui would die on her own and that it would be enough to sit back and wait.

But after the appearance of Tianzhu's yogic practitioners, Princess Yuansui was revived and carried off, and no one had expected this.

Yet, even so…

Qing had witnessed the battle between the Imperial Guards.

The guards with red eyes were like monstrous creatures from the Blood Cult, sent into a frenzy with some unknown technique, charging at the enemy with terrifying precision.

It was likely connected to the Heavenly Maiden Temple's sorcery, perhaps even something like brainwashed berserk warriors—warriors trained to be like fanatical soldiers.

But they were no real threat.

Their purpose was merely to restrain the enemy. If they were created through the Heavenly Maiden Temple's sorcery, it might have been a sort of performance test.

They appeared only after the resurrection artist's death, so whatever they created likely hadn't been fully tested.

The true power of the Imperial Palace guards, however, was revealed after they temporarily stalled the enemy.

This was a combat technique designed for an overwhelming one-to-many battle.

A sophisticated strategy and tactics crafted to deal with masters, particularly those beyond current martial experts.

Deploying snipers as part of this was a tactical masterpiece, one that took years—perhaps even decades—to perfect. After all, such coordinated techniques couldn't be perfected overnight.

Or perhaps, they had been refining it for generations since Wutian's times.

``You didn't know of those archers, did you? Even if you kill me, there's no way you'd leave the Forbidden City alive. Even if you killed me now, you wouldn't get away, would you?''

``Once you leave Beijing, how vast the world is. And once you acquire the skill, there's no reason to avoid the army. Just like what the Great Wutian did in the past.''

\textit{Ah, that Celestial Martial Emperor again.}

\textit{This pathetic old man was nothing more than a poor imitation of Wutian, the martial arts master who had once shaken the heavens and mocked the world, yet lived to tell the tale.}

It had been proven that such a person could exist.

For martial artists, Wutian was a god among them.

But to the Emperor, Wutian who had no Heaven above him, was merely a traitor to the world.

``Do you criticize me? Would you let go of your chance to become the supreme one? Would you remain a weak, unworthy man, trapped by trivial emotions, unable to become a true martial master?''

Qing snorted in derision.

``I can say this with confidence: if you're going to call a scoundrel like that a man of honor, then I'll never be one. You train in martial arts to protect those small virtues, but if that's not the case, then what's the point of training? Is it a hobby?''

If anyone knew Qing's hobbies, they'd understand that the words came from someone who indeed made good use of their martial skills in hobbies. That would be persuasive.

However, Duke Fan Yue didn't know Qing's hobbies.

``You already possess divine skills. You, who could acquire any power you desire, are surely capable of such feats.''

``What about you? Haven't you been coming and going from the Imperial Palace Martial Library? Isn't that where all the world's divine skills are gathered?''

``Is this what you, the successor to Wutian, the one who inherited his legacy, are saying?''

``Why do you keep bringing up that old man? He was never a man of honor to begin with.''

The Celestial Martial Emperor had left a profound and unimaginable shift in Zhongyuan.

The great truth was that no matter how powerful someone was, there was no way to touch them.

Even if that person was the sky itself.

The martial artists of the world had been given the greatest excuse to do anything they wanted—because once one became powerful, it didn't matter what they did, as long as they became a master, it was all forgiven.

But was Celestial Martial Emperor truly a ruthless, heartless figure who lived only for himself, abandoning everything else?

No.

He didn't care about others, but he didn't leave behind a world of destruction either. He didn't destroy the world; he carved a path for his own destiny.

Even the Blood Cult, the Demon Cult, and the Imperial Palace would have blood flowing if they acted out.

But ultimately, the Celestial Martial Emperor's legacy wasn't about living alone in solitude; he knew his limits and had to return to the world.

Because Celestial Martial Emperor was someone who wanted to be admired by the younger generations, he had trained himself to appear noble, even if it was only for the sake of future generations.

If someone was seeking admiration, it was surely an expression of affection.

After all, that's why people give advice.

The advice of elders comes from their own frustrations and failures, their desire to prevent others from experiencing the same.

``And above all, an honorable person does not make excuses.''

Qing let her sword hang loosely by her side.

After all, there's no fun in cutting down an old man who's already dying.

And besides, it would hurt more if she didn't.

The pathetic old man was still hoping that Princess Yuansui would end his life, expecting to die in such a pitiful and cowardly way.

It was a meaningless form of atonement, a self-serving end.

``To that child, you were once a kind teacher and a reliable protector, almost like a grandfather. No, she truly saw you as a family. You were that person once. But now, you're not. Now, you've drawn your sword on that child. Because you're jealous of her. Now, she's just an enemy who took everything that you think were yours.''

Qing laughed coldly.

``So, what's left now? Even if, as you wanted, you escape and eventually become an unbeatable master, what then? Who will be by your side? To everyone you knew, you're a traitor. What will you do, starting over? Trying to raise a new disciple? This time, a disciple you don't have to kill?''

Qing tossed her sword aside with a *clink*.

Duke Fan Yue stared vacantly at the sword that had fallen at his knees.

``At least Celestial Martial Emperor had a goal in his life, something he wanted to accomplish. If all you want is to live a little longer by taking others' skills, then what's the point of throwing away everything you already have to live like that? Terrible. If it were me, I'd just end it all right there.''

Qing turned away nonchalantly.

But even as she turned, her awareness remained heightened, sensing the shift in the surroundings.

She had no desire to die, especially not when there were still those she loved.

Of course, the worry was brief.

As she moved further away, the sense of someone with a reversed sword and raised arm came into focus—a final, desperate act, a person who had already thrown away their goal of living.

This was the last choice of someone who had nothing left to live for.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The traitor, Duke Fan Yue, was originally a descendant of the treasonous Jang family, who had infiltrated the imperial palace for an unholy purpose.

However, the young hero, Ximen Tianhua, had discovered the dreadful plot and, with loyalty, severed his head and presented it to the Emperor, who was greatly pleased.

In gratitude, the Emperor bestowed upon Ximen Tianhua the position of the Twelve Inspectors, recognizing her loyalty for the benefit of the country.

The officials had no reason to oppose this.

After all, it was a public service position granted to the man who saved the Emperor, and the traitor's family could only lament as they reluctantly accepted the Emperor's decision.

Qing, too, had no choice but to accept.

As Chunfeng had said, Qing tried to avoid it at first—saying she wanted to rest, even suggesting a position outside the capital to avoid the offer—but in the end…

``Should we not honor the hero who protected the Imperial Palace? Ximen Tianhua has done nothing but good, and we must reward her.''

The Empress's betrayal was clear.

After all, a mother would want to reward her daughter with a decent position, even if it wasn't a high one. Though the Twelve Inspectors' position was far beneath the princess's status, the Empress would be content, and it gave her an excuse to keep Qing around a few more days.

Thus, Qing's stay in the palace was extended.

Within the Forbidden City, in the Heavenly Maiden Temple.

Qing crossed the courtyard of the Heavenly Maiden Temple.

After all, she had something to ask Asiya, the head of the Temple.