\chapter{The Appearance of the Divine Dragon (12)}

There's a saying that even the most devoted son cannot care for his parents forever when they are bedridden by a long illness. How true indeed are the proverbs of old.

Qing thought to herself.

If the village's most intelligent man, Seol, had heard this, he would have scoffed and said, 'Hmph, how ignorant'.

This was because proverbs that were not accurate were simply nonsense and thus, naturally disappeared. Those that remained were based on the universal habits or psychology of humanity.

In Qing's hometown, this was also known as the 'survivor bias'. It wasn't that proverbs were particularly accurate, but rather that only the accurate ones survived and were passed down.

At any rate, among those around Qing, there was one person who was suffering from a long illness, to the extent that the proverb could be applied.

"Young Lady Moyong? Are you not hungry?"

Moyong Juhui stared blankly at Qing, then suddenly shifted her focus downwards. Qing, startled, raised her arm in a defensive stance.

These days, she felt a weakness in her chest.

"Ugh."

Moyong Juhui twitched, then abruptly turned her head away.

In truth, Qing also felt sorry for looking after Moyong Juhui.

Now that she realized that resolving grudges was not a universal method of mental healing, she felt like she had done something to be sorry for.

Still, these days, she had gotten much better, so when Qing said it was time to wash, she obediently followed along.

Since she trembled in fear whenever she saw a bathtub or a large basin, Qing had to bring her along and gently pour warm water over her to bathe her.

It was almost like caring for an old person.

Perhaps her efforts had paid off, as she no longer had seizures or screamed.

So she thought that if she cared for her a little longer, things would get better, but…

"Hey, Juhui. Aren't you going to join me today?"

"Ah. Sister Choryeo……"

"Aren't you going to eat? They say you should eat more when you're sick. You should eat hearty meat to gain strength."

It was Paeng Choryeo.

It was remarkable that Paeng Choryeo, who had never spoken to Moyong Juhui since she was rescued, was now talking to her, who had buried her head between her legs at the training grounds every day ever since.

Paeng Choryeo was kind, but she did not usually show much interest in others. Since the women of Jianghu always approached her first because of her brilliant younger brother, she never had to approach anyone first.

So, she had never really paid attention to Moyong Juhui's strange behavior, as she used to follow Paeng Daesan around anyway.

But as the days went by, she finally took a little interest.

Is she a bit strange? Why doesn't she ever eat with us? Qing doesn't seem like someone who would ostracize others, and she doesn't give off that vibe either. But she just keeps watching. Does she seem sick?

Then, Moyong Juhui immediately agreed.

"I will. Thank you for your concern."

She even smiled!

And she even clung to Paeng Choryeo's arm, linking arms with her.

"What the hell? Your arm is so soft. Have you lost all your muscles? Have you been starving yourself lately?"

"I, a little."

"That's not good. You should eat meat. If you build up your muscles, you won't get sick. You're sick because you don't eat."

"Yes. Ri, Right."

Seeing that, Qing couldn't help but feel a bit upset.

She felt half betrayed and half resentful.

Of course, she hadn't been looking after her to hear thanks or be treated as a benefactor, but she had been kind and attentive, yet she had been ignored.

But the moment Paeng Choryeo, who had always been indifferent, said something, she clung to her happily. How could that possibly look good in her eyes?

And so, she took a seat at the dining table and watched as Paeng Choryeo diligently fed her not just any food but only meat, which Moyong Juhui happily gobbled down like a baby bird.

It was a good thing Dang Nana wasn't there. If she had seen this, she would have said, 'What the hell is that?' and thrown her poison, not even her hair.

So, in the end, Qing thought to herself.

What the hell? She seems perfectly fine?

Was she just acting up because she thought I was easy, since I was always saying yes to everything? Did she find it fun to see me flustered, not knowing what to do?

This is why they say not to take in dark-haired creatures.

What? They say that again? So what……

Half of her felt this way.

And the other half thought, 'Maybe I'm actually hindering her recovery'.

After all, whenever she saw me, she would be reminded of the underground, so if she kept seeing me and recalling bad memories, of course, her condition wouldn't improve.

Combining the two, Qing eventually gave her a notice of departure.

"Young Lady Moyong, shouldn't you be returning to your family soon?"

"……Huh? W-Why?"

"Well, your family must be worried. And as you can see today, yes, you probably find it hard to look at my face, right? I couldn't even think that way. I'm sorry, I kept making you recall bad memories. I didn't think that way. Hmm. I'm sorry for being so nosy."

"No, wait, just a moment. That's not it-"

Moyong Juhui reached out her hand as she spoke.

This bitch, she's at it again! I won't be fooled twice!

Qing swiftly distanced herself and defended her weak points.

The first time, Moyong Juhui was just grabbing onto her because she was in a hurry while being carried, so she didn't count it as an attack.

However, the second time, she clearly laughed at her pain, didn't she? Since her intent was proven, it was right to consider it an attack.

Moyong Juhui, who had missed her target, looked even more hurt than when she had failed her attack.

"Young Lady Moyong, you shouldn't do that. Do you know how much it hurts? I won't blame you for what happened in the past. And your toes have all healed now, haven't they?"

"They're still! They still haven't grown back yet-"

"Even so, it's not like you'll be showing your toes to anyone as long as you're with your family, right?"

"That, um."

Then, there was a knock and a 'Tsk tsk' sound from outside. It was the sound made by the Muchon Pavilion's handmaiden.

"Yes. Please speak."

-Young Lady Gongson has arrived.

"Ah, has it been that long already? I almost forgot. Wait, no. I'm going now."

Then, Qing spoke to Moyong Juhui.

"I'm sorry for being so nosy. Well, as soon as you make it to the finals, we won't see each other anymore. I'm sorry for what happened in the underground. I was just trying to help, but I really, truly didn't think Young Lady Moyong would be so shocked. Well then, I'll take it that you're going back."

After saying that, Qing left the room.

It was the first time she had seen Gongson Yoye since the semifinals.

As soon as she saw Qing, Gongson Yoye's face brightened.

The undisguised delight was a pleasure for Qing's heart.

"Ye! What kept you so busy that you didn't even show your face? I thought you were being cold-hearted because we're supposed to meet in the finals."

"How could that be? But friends are one thing and the finals are another. If I win, um, then, we'll still be friends, right? No, no, no, of course, it's not like Young Lady Ximen would ever do such a thing, but since this is such a big martial competition and all, so the results might, no, no, no, please pretend you didn't hear anything."

"Hmm. You're full of confidence, aren't you? To already be worrying about what happens after you win?"

"It's not like tha-."

"Hey, it's a joke. How could our friendship be affected by something like that? But, what kept you so busy?"

"Haa……"

At that, Gongson Yoye let out a deep sigh.

"I thought I just had to swing my sword diligently, but I had to greet all sorts of people. I didn't realize that the wishes of a clan were such a complicated matter."

Then, she told the story of being called here and there to offer greetings. She also learned about the complex behind-the-scenes negotiations to fill the vacant spots in the new Ten Great Clans.

"Cheonil too, though I feel bad for saying this, I sometimes thought he was enviable. I had never left the training grounds before coming here, but Cheonil was always out and about, so much so that he was rarely in the clan. But that wasn't the case."

Gongson Cheonil's marriage had been arranged and the other party was the eldest daughter of the Sama Clan.

"She's older than me, and, well, to be honest, she's an ordinary person. Though I feel bad for saying this. I thought Cheonil would be matched with a more beautiful and younger lady."

"So it's an arranged marriage……"

"Yes. That's right."

"How's Cheonil?"

"It's a marriage arranged by Cheonil himself. He said he would do his best. After all, people don't live just by looking at each other's faces and growing fond of one another……"

Just as Gongson Yoye had lived her entire life inside the training grounds, Gongson Cheonil had lived for the sake of his clan's wishes.

"Mm. If he chose it himself, there's nothing we can say about it. But the Sama Clan? Then, did you see that person? The one they call the Sagacious and Beautiful?"

"Ah. My new sister-in-law. I haven't been able to talk to her."

"I heard that this is quite amazing here."

Qing asked, tapping her own chest.

Then, Gongson Yoye tilted her head.

"Not really? When I saw her, she wasn't particularly remarkable."

She had heard that she always wrapped herself up to hide it, so Qing just accepted it as such.

After chatting for a while, Qing cautiously brought up the main topic.

"So, you know. I heard that Ye uses Innate True Qi in her martial arts? Is that true?"

"Ah. How did you know……"

"Sanie said something like that. So it's true."

Gongson Yoye nodded.

"Since we have sparred many times, you might have noticed a difference in our sword prowess during the competition. But Young Lady Ximen, to be precise, it's not a martial art that uses Innate True Qi, but one that can. Usually, it's not used to that extent, so don't worry."

Qing immediately understood.

It was a technique that could be toggled on and off.

"But that consumes one's lifespan, doesn't it? Does she really have to go that far for a mere competition?"

"Mere, you say?"

Gongson Yoye looked at Qing with an incredulous gaze.

"Even if it's for the sake of my clan's wishes, I hope Ye won't have to resort to using her lifespan. Does she really have to win that badly? Is there some kind of agreement for her to enter the Ten Great Clans immediately if she wins?"

"It's not like that."

"If Ye really, truly has to win no matter what, then there's no need to consume her remaining lifespan. I can, um. We can fight for about twenty rounds, no, make it a bit more intense and go for forty rounds-"

"Young Lady Ximen."

Gongson Yoye's expression turned cold.

It was the first time Qing had seen such an expression.

When they first met, she had a gloomy and forlorn look, and after they became friends, she always wore a smile.

"Do you think I am that pathetic?"

"Huh? No, that's not what I meant-"

"Then what is it? Do you pity me? Because I'm a fool who has been trapped in a training ground all my life, not knowing the ways of the world and only swinging a sword? Is that why? Was Young Lady Ximen's friendship with me nothing more than pity for a poor person?"

Qing was greatly taken aback.

"No, I… That's not what I meant. It's just a competition, so why would Ye have to risk her life like that? I want Ye to live a long, long time and I want to see her for a long time, but using up your lifespan for such a thing is too wasteful."

"Just a competition, you say?"

Gongson Yoye's anger grew even more intense.

"To Young Lady Ximen, yes. It might just be a pastime where you can win if you feel like it, since your achievements are not low."

"Ye, that's not what I meant-"

Qing kept repeating herself.

However, Gongson Yoye cut her off.

"But it's not like that for me. I have lived my entire life for this moment. You might laugh at a mere twenty-seven year old wench talking about her entire life. But still, my entire life, my entire life, I have truly lived only for this one chance. But to Young Lady Ximen, it was nothing special, huh? I was the one risking my life."

"Ye, wait a minute, calm down."

"How could you look down on a person like that. Ha. Serves me right. How could I possibly have a friend like you? Young Lady Ximen? This isn't friendship. It's just playing friends. Why, was it fun? To give just a bit of your worthless friendship and see me cling to it? I have never begged for friendship, nor am I pitiful."

Qing was just at a loss for words.

W-Why? Why is she suddenly exploding like this?

What did I do? What did I do so wrong? 