\chapter{The Appearance of the Divine Dragon (11)}

Sima Chunbong believed that everything had a grand scheme.

To be precise, she asserted that there was a grand scheme in the world
that only a few geniuses could perceive.

And since Sima Chunbong believed herself to be a super-beautiful
woman, belonging to the very highest class of those few, she thought
that she alone reflected on the grand scheme while everyone else only
saw fragments of incidents.

Thus, she gathered information from the events of the Martial Arts
Tournament, piecing them together to identify individuals whose
actions before the consecutive murders in Kaifeng Prefecture were
suspicious.

And as a result of focusing on the connections among those individuals,
she concluded that an entire group, a band of vagrants who had
advanced to the finals, was extremely suspicious.

It was because these poor bastards, who had been frequenting cheap
eateries every day after advancing to the finals, suddenly stopped
going out and remained within the Martial Alliance, disappearing from
the records.

In truth, Sima Chunbong was indeed smart.

Her title, the Wise and Virtuous Flower, was not given in vain. It wasn't
just some random title given because they needed to come up with
something for each of the Five Flowers of Wulin, like, 'Sima is known
for her intellect? Then, let's just call her the Virtuous Flower or
something'.

She was known as the Wise and Virtuous Flower.

Her name might sound a bit old-fashioned.

At any rate, at a young age, and as a woman, she was assigned the
duties of the Martial Alliance's Vice-Military Advisor. She handled the
workload with ease and was able to focus on her other interests,
showcasing her capabilities.

Having accurately grasped the tail of the incident, Sima Chunbong let
out a sly chuckle.

By revealing the truth of this incident, she would take a step closer to
her grand dream of becoming the first female and youngest Chief
Military Advisor of the Martial Alliance.

And the vagrant group had started frequenting cheap eateries again at
some point, a fact she had confirmed today through the guards at the
main gate.

"Yes. It was strange from the beginning. Vagrants are just a nicer way
of putting things, aren't they? Beggars, paupers, vagabonds, rolling
bones of stray dogs, and so on. One could use any of these terms
instead and it wouldn't be strange at all. How could such rootless
individuals advance so far in the Hidden Dragon Sparring Competition
and achieve such miraculous results?"

Sima Chunbong muttered to herself like a madwoman.

Of course, she always muttered to herself, asserting that speaking her
thoughts aloud was the true quality of a wise person.

"No. It's impossible. This must be the work of some force trying to
infiltrate the Orthodox Wulin with their spies. Thus, I, Hyunhwa Sima,
must uncover this terrible and vile conspiracy and reveal my brilliant
mind to the world. Yes. Indeed."

Though the intentions and process of her deduction were extremely
impure, Sima Chunbong had, in fact, accurately grasped the truth.

Thus, she dressed up nicely, put on makeup, and headed to the
marketplace, where she found a cheap eatery with a sign that read 'Leisurely
Restaurant'. The place was already noisy with loud chatter.

"The strategy of using a beautiful woman is also a type of scheme that
is like the destiny of a woman born to be a strategist. Let's go, Sima.
To lead this world filled with fools with wisdom, I must endure the
humiliation of catering to those vile creatures."

As she made that solemn and serious vow to herself, a child passing by
expressed their thoughts.

"Mommy, Mommy. That Unni. She's just muttering to herself."

"Shh. You shouldn't do that. There are people who are a bit sick in the
head, you see. Tsk tsk. What a pretty young lady, what a shame."

At any rate, having steeled her resolve, Sima Chunbong was about to
lift the簾 of the eatery when she suddenly stopped.

"Wait. Could this be? It's strange. Could it be a trap? How, how could
people possibly eat in such a wretched pigsty? Is this even a
restaurant? Could it be a front for some kind of underground
organization? It's suspicious, very suspicious."

Sima Chunbong hesitated for a moment.

She had heard unbelievable rumors that commoners in the Central
Plains lived on just a few silver coins a month, but she couldn't imagine
even the poorest, dirtiest, and most foolish commoners of the Central
Plains would eat in such a hideous place.

"No. I can do this. I must."

For the peace of Wulin.

But more than that, for Hyunhwa's honor!

"Where is there a strategy without risk?"

With a grand determination, Sima Chunbong carefully lifted the dirty
簾 with her fan, taking care not to touch her body as she cautiously
infiltrated the suspicious eatery.

Since the vagrant martial artists had practically rented out the place,
the moment Hyunhwa entered, their eyes were immediately drawn to
her.

It was mostly because her lower body, hidden behind the 簾, blocked
the entrance as she hesitated, causing everyone to glance over to see
who it was.

Thus, when a beautiful woman appeared, even if her eyes were a bit
fierce and her pupils were small, giving her a somewhat sinister and
evil impression, the vagrants couldn't help but gape.

Enjoying their gaze, Sima Chunbong greeted them politely.

"Oh my. If it isn't the, um, not-so-renowned but perhaps with some
potential to become so, competitors of the Hidden Dragon Sparring
Competition, who are not exactly experts…… nor Great Experts, uh,
um. Young Experts?"

Her polite greeting made the expressions of the vagrant martial artists
subtle.

What the hell? Is she trying to pick a fight or something?

"If it isn't too rude to ask, who might you be, Young Lady……?"

"Ah. I am known as Sima. Those in the Wulin who are familiar with me
call me the Virtuous Flower, as I am quite wise."

And then, one by one.

"Wise and Virtuous Flower!" "Sima Chunbong!" "Three Perfections
Beauty!"

Sima Chunbong's eyebrow twitched, its angle becoming subtly sharper.

Among those, Sima Chunbong only acknowledged three words:
Hyunhwa, Sima, and Beauty.

Three Perfections Beauty was one of Sima Chunbong's many titles.

Since Sima Chunbong had many titles.

Three Perfections Beauty meant a beauty who was outstanding in three
aspects, and this was also a title that Sima Chunbong detested.

To think she was only perfect in three aspects when she should be
called the Ten Thousand Perfections Beauty or the All Perfections
Beauty, with everything perfect.

Moreover, one was her intellect, and the other two were unspeakable
and mortifying mockeries.

A few other minor nicknames were mentioned, but she ignored them,
deeming them not worth addressing.

Originally, Sima Chunbong was someone who pretended not to hear
what she didn't like, even if she heard it.

"Such excessive praise. Just Hyunhwa is enough. Or you may call me
Young Lady Sima."

At that, the eldest of the independent martial artists, the Earthly
Strong Fist Master Ma Yeongjeon, asked on their behalf.

"Um. If you'll excuse me, are you perhaps the person you claim to be?
You seem a bit different from what I've heard."

"Yes. That is extremely rude."

Sima Chunbong huffed and continued.

"Since we will soon become members of the Orthodox Wulin, what
would I gain by deceiving you? If you are truly suspicious, you may
come to the Military Department and request an audience with the
Vice-Military Advisor. Of course, as insignificant as all of you are, you
wouldn't dare to do such a thing, but still."

"Um. Your appearance might be a bit different from what I've heard,
but you are indeed the foul-mouthed beauty, Young Lady Sima."

She was known throughout the world as a foul-mouthed person, and
indeed, she looked the part.

Moreover, since she had a vicious beauty, just as rumored, the
description was convincing.

As for the biggest characteristic, well, that could be hidden, after all.

"So, why have you come to such an insignificant gathering of
insignificant Young Experts?"

The vagrants' reactions were not great.

Sima Chunbong was taken aback.

Why is this happening? Shouldn't they be on their knees, licking the
ground like dogs at the sight of this beauty?

In truth, it was all because of Qing.

If they hadn't encountered Qing's divinely beautiful appearance, they
might have thought, 'Yeah, I guess if she's pretty, she can get away
with being a bit rude'. But they had already befriended a greater beauty,
so they had no reason to feel desperate.

"Hmm. Ahem. This Hyunhwa has a straightforward manner of speaking,
so I hope you can understand with generosity. After all, the truth is
often bitter."

"Cough."

"Anyway, I came here to celebrate with the insignificant Young
Experts on becoming members of the Orthodox Wulin, didn't I? It is
like a dragon rising from a ditch, so you will not remain insignificant
forever, will you? Though the chances are low."

Even though her words were utterly impolite, it was a celebration, so
they couldn't exactly cold-shoulder her.

Moreover, since the Wise and Virtuous Flower was rumored to be the
likely candidate for the next Chief Military Advisor of the Martial
Alliance, it was a great opportunity to build a connection.

Ma Yeongjeon's eyes conveyed such a message as he glanced at his
fellow vagrants.

The vagrant comrades also agreed with that sentiment.

"We are humbled by your presence in this lowly place."

"Indeed. This place is quite lowly."

"……"

And so, she graciously approached, personally pouring drinks for
everyone.

Her words were rude, but her actions were polite and her face was
beautiful.

Since a high-ranking woman had approached them first and poured
them drinks, the initial discomfort melted away.

With this, the realization that they had indeed joined the Orthodox
Wulin sunk in.

Thus, with the fairly ordinary toast of 'For all of our success', they
drained their cups, only for Sima Chunbong to exclaim.

"Oh my! Put down your cups, everyone! The alcohol is sour, smells
awful, and tastes terrible! Even pig's piss would taste better than this.
This must be poisoned!"

Of course, there was no way that the alcohol they had been drinking all
this time would suddenly be poisoned.

"……We apologize. The alcohol is cheap."

"Oh my. Goodness. How could this be. How can people live such
miserable lives and drink such, no, it is an insult to even call this
swill, alcohol?!"

"……"

At that, the vagrants began to regret their decision.

They should have just said they would drink amongst themselves and
refused her offer.

But that regret soon disappeared.

"Haa. This won't do. Today, this Hyunhwa will show you what proper
alcohol is. Since you are all from such humble origins, you likely do not
know the taste of true alcohol. Let's just throw away this pigsty or
demolish it, whatever, and head to a proper restaurant."

Although her words were utterly impolite, it was a declaration that she
would treat them to a nice meal.

At that, the vagrants cheered in unison.

Sima Chunbong smiled wickedly.

As expected, those of humble origins and ignorant humans are so
simple-minded.

Now, it is time to uncover all the truths entangled in this incident.

And Sima Chunbong achieved her goal.

However, it was not right to criticize the vagrants for having loose lips.

In fact, what they revealed was mostly praise for Qing, about 99\% of it,
which had already been coordinated and embellished.

It was just that no one would turn down free drinks and food from a
beautiful woman, especially when they were practically begging to
share the story of how they had repaid her kindness.

As such, it was only natural to say, 'Sigh, this is a secret, but…' when
someone was crying and begging to be told.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It seems Gongson Yoyae is busy again today.

And Namgung Shinjae and the Peng siblings are never not busy.

Especially when Namgung Shinjae and Peng Chaoryeo are together,
the heat of their training reaches its peak. By the time the sun sets,
Qing would be drenched in sweat.

Handing over a cotton towel, Dang Nanah grumbled.

"Ha. That girl is still doing that. Doesn't she ever go home? Isn't she
perfectly fine walking around now?"

Moyong Juhee was still sitting under the wall, burying her head
between her knees.

Although her toenails had not fully grown back, they had healed well
thanks to the miraculous medicine of the Tang Clan.

Having four of her molars extracted was a lot in terms of numbers, but
since they were the ones at the very back, one from each side, top and
bottom, it wasn't noticeable.

Originally, Ximen Surin had suggested that the Moyong family should
be informed, but Qing opposed it, saying that it was for her to decide.

After all, everyone had things they didn't want to reveal, especially to
their family.

Ximen Surin had stroked her head, saying, 'How could my disciple's
heart be so considerate and beautiful?'.

However, Dang Nanah was not at all pleased with this.

Even if she had suffered harsh torture and was hurt, did that mean she
could vent her anger on others? And why on the chest of all places?

Though thinking about it, it wasn't because it was her chest but rather
because it was Geomhwa's chest that she vented her anger there.

At that, Qing smiled awkwardly.

"What? Young Lady Moyong? Don't be like that. Young Lady Moyong is
sick, you know."

"Hmph. Why don't you show such dedication to me? I'm your friend,
you know?"

"You've already passed that stage, Nanah. We're old friends, a true
friendship. Why would we need to put on airs and act all dignified? We
have eaten together, bathed together, slept together, and done
everything together, haven't we?"

"Cough. Well, if you put it that way……"

Dang Nanah turned her head away in embarrassment.

Why is it that she can say such things without even changing her
expression?

Then, Qing suddenly had a thought.

Dang Nanah is one of the Five Flowers of Wulin. So is Moyong Juhee.
Young Lady Jinseol has a lot of exposure, and I want to be friends with
Young Lady Seol, but I haven't had the chance……

Then, isn't there one missing?

"Um. Speaking of which, they say there are Five Flowers of Wulin. I
haven't met this person called Hyunhwa. What's she like?"

"Hmm? Exceedingly Insufficient?"

"Exceedingly Insufficient? That's quite a harsh evaluation, isn't it?
Why?"

"No, it's one of her nicknames."

"What is she like to have such a nickname?"

"She's got a lot of these. They say her chest is this big."

Dang Nanah made a gesture of hugging a tree. Her fingers barely
touched, indicating the circumference.

"What? Really?"

"I've only heard about it. She hates it so much that she apparently
binds it so tightly that she can hardly breathe. I've only seen her twice,
so her clothes didn't really stand out to me."

And then, she continued.

"Three Perfections Beauty. Excels in intellect, this and that. They call
her the Wise and Virtuous Flower, you know? They say it's a wisdom
pouch. Pfft. Apparently, it holds at least ten thousand volumes worth of
wisdom. She knows it too, so she hates it and tells everyone to drop the
'wisdom pouch' and just call her the Virtuous Flower."

"But how big is it exactly to get such a nickname?"

Hmm. Just what scale does she have to earn such a nickname?

Hmm. I'm really curious about it.

I'm really, really curious about it.

Qing gulped. 
