\chapter{The Appearance of the Divine Dragon (13)}

Large droplets began to form in Gongson Yoyae's deer-like eyes.

It was a wonder they managed to cling on without falling, but eventually,
they slid down the curves of her face.

And then, she burst into tears, sobbing as a torrential downpour
suddenly fell.

"Sometimes… No, almost all the time, I wanted to give up everything
and just live like an ordinary woman. B-But I endured it all for the sake
of my long-cherished wish. I endured. But for it to be trampled so
cruelly……"

I think I really touched neilin there.

Neilin meant a reverse scale. It was said that dragons had
one such scale under their chin.

Even though a dragon's patience reached its limit after thousands, tens
of thousands of years of asceticism, the moment their neilin was
touched, they would fly into an extreme rage, unable to control their
anger. They would become mortal enemies with whoever touched it,
even if it meant falling from grace and becoming an Imoogi again.

That was what it meant to touch one's neilin.

And Gongson Yoyae's neilin was being disregarded as a martial artist.
Gongson Yoyae's life was forged solely as a martial artist.

Therefore, disregarding her as a martial artist was perfectly
synonymous with disregarding her entire life.

Qing was greatly taken aback.

Why, why is she crying? Is it something to cry about?

"Yes. Wait a minute. Wait a minute and calm down. Huh? Why don't we
take a few deep breaths?"

"How co-."

"Now! Here!"

Qing quickly cut off Gongson Yoyae, who was about to explode again,
by shouting loudly.

Then, she shoved a box into her hands.

"Stop. Stop crying. Here. When your Innate True Qi is damaged, it is
good to take elixirs. I specially prepared this for you, you know?"

"I don't need somethi-"

"Ah-ah. It's a Grand Rejuvenation Elixir, you know? A Grand Elixir from the Shaolin
Sect. You know, right? It's not 'something'."

Gongson Yoyae froze at those words.

Of course, she was still crying, so she did hiccup, reflexively inhaling
through her nose.

"Grand Elixir? A-Are you teasing me? Or is it really… hic, a Grand
Elixir?"

"It's really a Grand Elixir. Great Master Wunue personally gave it to
me."

"Why would Great Master Wunue……?"

"I told him I had a friend whose Innate True Qi was damaged, so he
readily gave it to me. It wasn't that hard to get, so you don't have to feel
too burdened by it."

Gongson Yoyae's mind cleared in an instant.

It felt like cold water had been poured over her.

"You're giving this, this to me? Such a precious, this is far beyond
precious……"

"I got it for you in the first place, you know?"

Gongson Yoyae attained a great realization.

This person, to this person, not only the Hidden Dragon Competition but
all the wealth and honor of the world are nothing.

A Grand Elixir was considered a treasure that was worth a spare life.

Just revealing its possession could put one's life at risk.

But here was a person who casually pulled out such a treasure and
handed it to her. And it was because she was worried about her friend's
lifespan, her Innate True Qi, over such a treasure.

The Hidden Dragon was probably not even in her mind
from the very start. So how must she have felt when she heard that
Gongson Yoyae was going to use her Innate True Qi for it?

As such, Gongson Yoyae's explosive anger, which had burst like
fireworks, ended up destroying her own house.

And after that realization, boundless shame washed over her.

"Um, that. Young Lady Ximen? I'm sorry. I, I said some harsh words.
What should I do? I, I don't think I deserve to be friends with you in the
first place. Young Lady Ximen is so considerate of me, but I doubted
you. How can I call myself a friend? I don't even deserve to have friends
in the first place, a wench like me-"

"Hey, it's okay. People fight with their friends sometimes. Mm. To be
honest, I did think you were pitiful. But that's not why we became
friends. Then would I have to befriend every pitiful person in the
world?"

"No. It's because I'm like this that I don't have any friends. I'm sorry,
I'm sorry……"

"No, it's okay, I said."

Afterward, Qing continued to soothe Gongson Yoyae, who kept trying
to dig herself deeper into the ground.

Honestly, this was the third time Gongson Yoyae had exploded. She
was usually quiet, but when she got angry, she tended to explode
abruptly.

The second time was when Qing gave her the hairpin.

This was the third time.

And the first time was before Qing even arrived, during the Dragon
Phoenix Assembly, when she had given a very sharp criticism to the
members of the Phoenix Assembly who were acting like silly girls.

I can't believe you're calling this a gathering of martial artists when all
you do is dress up like idiots and talk about seducing men. Are you
actually a gathering of prostitutes?!

If the members of the Phoenix Assembly hadn't treated Gongson
Yoyae like she was invisible, trying to act like she didn't exist…

At any rate, Gongson Yoyae was firmly broken due to her shame,
embarrassment, and fear.

As such, it took quite some time for Gongson Yoyae to calm down,
apologizing like a sinner all the while.

"I can't accept this. I am grateful for your kindness, but I cannot handle
such a treasure. As you know, Young Lady Ximen? It is said that
unmanageable treasures bring forth blood."

"Then, can't you just eat it now?"

Gongson Yoyae smiled at that.

Her eyes were so swollen that the smile was a bit unsightly, though.

"I will reach the Transcendent Realm, so I will be fine. And our family
has also prepared elixirs. I can't just use my Innate True Qi without
any countermeasures, you know?"

"Ah. I see, I guess so. Still, keep it and use it later when you're in
danger-"

"No. I can't accept it."

Then, she clasped Qing's hands and spoke earnestly.

"I truly wish for you to do your best in the finals of the Hidden Dragon
Competition, Young Lady Ximen."

"How can I swing my sword at you when I know you're using your
lifespan?"

"Young Lady Ximen. I have been truly looking forward to the finals of
the Hidden Dragon Competition. I truly, truly want to cross swords with
you with all my might. That is how much I have been looking forward to
it. You said you would not look down on me, so that is why I became
angry."

"But how can I do that when I know you're obviously burning away your
life?"

Then, Gongson Yoyae looked directly into Qing's eyes. Since she didn't
usually make eye contact, it was clear she was being very sincere.

Of course, her red, swollen eyelids made the picture a bit peculiar,
though.

"Will you do that for me? I think that would make me happy, even if it
was only for a short part of my life. Please, I ask you to be there for the
moment I have looked forward to the most in my life. Okay?"

At such earnestness, there was nothing Qing could do but nod.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing was not from Zhongyuan.

She was also someone who had suddenly fallen into this strange place
from a world where the value of a community called roots was far
inferior to that of an individual.

As such, Gongson Yoyae's outburst was nothing more than a sudden
rage to Qing.

However, objectively speaking, Qing was at fault.

If Ximen Surin had heard this conversation, she would have shed tears
and given a harsh scolding, the kind that would make one's head spin.

What Qing had said was roughly this:

Why are you risking your life for just a Hidden Dragon Competition?

Don't waste your precious life on such a petty trick. I'll just forfeit
instead.

However, Gongson Yoyae had truly risked her life.

All her past life and ascetic training were preparations for this very
moment.

Therefore, Qing had denied Gongson Yoyae's entire life.

Moreover, it was an even more painful betrayal because she firmly
believed and relied on Qing to be her only friend.

If it had not been for a treasure like the Grand Elixir, she would never
have even considered Qing's sincerity.

It was such a painful and bitter betrayal.

But Qing still could not understand.

What in the world was the Hidden Dragon Competition? No, even more
fundamentally, what was a family?

Why was she risking her precious life for her family?

Why was it so important?

Why was it not a family for the sake of people? Why were people
sacrificed for the sake of the family?

It wasn't even like the Gongson Clan was on the verge of collapse or
living in some dilapidated hut.

It wasn't one of the Ten Great Clans of Zhongyuan, but it was still
a famous and large martial family.

Officially, her surname might just be Gong, but everyone actually called
her Gongson unless they were trying to start a fight.

Honestly, this was the same for a sect instead of a family, so Qing's
fundamental way of thinking was different from that of the people of
Zhongyuan.

And Qing felt it keenly.

"It seems Young Lady Gongson has a great deal of self-control to not
have drawn her sword. If you don't wish to make an enemy, don't say
such bullshit carelessly."

"Cheonga was in the wrong this time. It's like telling a kid who trained
all her life for the competition to just give up. How could she not get
angry when she's been making such an effort for her family's
long-cherished wish?"

"Hmm. Sword Friend, I didn't expect this, but I am disappointed. I
think it might be worth considering downgrading you from Sword
Brother to Sword Acquaintance."

These were the reactions of Peng Daesan, Tang Nana, and Namgung
Shinjae respectively.

So this is something to be that angry about? I wonder.

Then what's a Sword Acquaintance?

Honestly, I don't really get it.

If it was me, wouldn't it be better for her to dress up prettily and me to
naturally just lose so that she wouldn't have to use her Innate
True Qi?

What is it to be a martial artist? What the hell is a job where you have to
use all your might as a martial artist?

It's just a business where you use martial arts and are hostile yet equal
to the government, so you can gallivant around proudly.

Um. Isn't this just a cartel?

Anyway.

Can I really swing my sword with all my might in the finals?

What does it even mean to swing a sword with all my might when she
clearly knows she's burning away her lifespan?

What does it even mean to swing a sword with all your might in the first
place?

Isn't martial arts for cutting enemies?

So, if it's not a Life-or-Death Duel where you take a life, if it's not
drawing a Life-Taking Sword, isn't it impossible to even put all your
might from the start?

A sword is for cutting.

Self-defense to protect myself.

A barrier to protect those I like.

A tool to cut down bad guys and have fun.

But how can there be a duel where you have to put all your might into it?

Does it make sense to use a Life-Taking Sword in a duel to determine
victory or defeat? Does that mean it's not all your might if you don't use
a Life-Taking Move?

These were questions she had never pondered before.

They were also questions that would not be answered even if she
thought about them.

However, Qing had one advantage that was also her greatest
shortcoming.

If she didn't know something, she didn't try to figure it out on her own.

Instead, she just asked someone else.

If there was no one around to tell her, she would just think about it later.

That was why her ignorance never improved.

Anyway, so Qing asked.

"Master, what is martial arts?"

"……? Why do you ask that now?"

Ximen Surin was startled.

Every martial artist held their own sword in their heart. Ximen Surin
used the word sword because she was a sword user, but that meant
everyone had their own definition of martial arts, which they forged
straight in their hearts.

That was why martial artists lived by drawing their own swords, thus
illustrating their meaning and will in the world.

That was also why martial arts was called 功夫 (Gongfu).

But to think that a Master who had reached the Late-Stage Peak
Realm would ask such a question.

It was a question that was far too late, as one could not cross the
threshold of the Peak Realm without properly drawing their own sword.

But it was fortunate and commendable that she was asking, even if it
was late.

And she was still young, so it wasn't really that late.

Ximen Surin's blind affection for her disciple was growing thicker by
the day.

"Everyone's martial arts are different, so this master cannot forcibly
speak and impose it on you. But what was the reason you trained in
martial arts, Disciple?"

Then, Qing pondered for a moment before answering.

"Um. To survive?"

Qing's martial arts was a means of survival.

And it was still ongoing.

When she reached the Late-Stage Peak Realm, she was so proud of
herself for becoming a Master, but lo and behold, Transcendent Realm
Masters kept popping out of nowhere and Unrestrained Realm Masters
appeared every now and then.

"I see. You said you were a ronin."

Ximen Surin nodded at that.

"It is only natural for my disciple's realm to have not increased. It is
good and fortunate that you have come to ponder this now."

"Um. Is it that important?"

"Of course. It is important. You have to clearly establish what martial
arts is to you and why you wield a sword. Otherwise, it is no different
from walking a rough path with your eyes closed, even if you are looking
straight at your goal." 