\chapter{The Appearance of the Divine Dragon (4)}

The foundation of Shaolin lies in an unwavering heart. According to Buddhist law, one should strive for an unwavering enlightenment, unmoved by any temptation. They do not get excited over joyful events or easily give in to anger. Moreover, they abstain from being with women throughout their lives, distancing themselves from worldly pleasures. As such, joy, anger, sorrow, and pleasure are mere illusions, and temptations are called colors (色), which are illusions. The material world itself becomes the saha world.

Thus, there is the Buddhist teaching that form is emptiness and emptiness is form, meaning that temptation is, in fact, nothing, and only when one empties oneself does the color (world) truly fill the heart.

Therefore, the martial arts of Shaolin are like Mount Tai. It is the heaviest mountain in the world, steadfastly maintaining its place with an unshakeable heart and an indomitable body in the face of any hardship.

Thus, the Great Master Wunue\footnote{無虐; lit. 'No Calamity'; Muhak in the original text}, the foremost martial monk under the heavens, was simply sitting heavily in his place. Even when his immature disciple displayed arrogance due to his pride, he simply chanted Buddhist sutras and steadied his mind.

After all, what could one expect from a young man who had just set foot in the world? Would a still young and naive person listen to admonishments? He thought that later, the disciple would realize his own shame and correct his behavior.

However, when the increasingly immature disciple wildly swung his fists, spraying Force Compression everywhere, the Great Master's expression gradually hardened.

Of course, Ximen Surin's disciple had already shown what she was capable of, so it wasn't a fatal move that would endanger life.

In fact, Weifeng was also confident in Qing's resilience, which was why he unleashed such powerful moves.

But even if he won like this, what would be the point?

If he really hit her, even if his life wasn't at risk, she would have to lie down and recuperate for several months. Moreover, the bastard disciple was even aiming for the face without hesitation. If her nose was broken or her jaw was shattered, she would have to live with a lifelong grudge.

Even so, the Great Master endured. He thought that the disciple just hadn't experienced true frustration yet, having only trained in the mountains without any real rivals of his age.

However, this time, he could not endure any longer. The Great Master's eyes widened as he abruptly stood up from his seat, took a quick step forward, grabbed the railing, leaned his upper body forward, and stretched his neck.

Beside the Great Master, the Shaolin monks in their golden kasayas lined up in a row in the same posture. The Great Master muttered, as if possessed.

"The majestic sound of the heavens pervading all of the dharma realm. Even the greatest giant under the Brahma heavens is but under the palm of Buddha……"

It was a record of the lost supreme technique of Shaolin. When the Great Master saw it, he thought it was just a Zen riddle, full of hot air instead of describing the characteristics of the martial art. However, upon encountering it, he found that it was a precise and clear explanation unlike any other.

Brahma meant all the heavens, the universe, of the three thousand great thousand worlds. As such, the sound of the Brahma bell was the law of enlightenment that echoed throughout the entire world at once.

Thus, no matter how great a human might be, they were ultimately just one of the countless beings in reincarnation. How could they compare to the greatness (太) of Buddha, who transcended such cycles?

Such was the palm of the Tathāgata, which was like the solemn will of heaven. It was natural and just that the will of heaven should resonate with the sound of the Brahma bell.

"How! I-Is that not the Tathāgata's Palm?!"

At the martial monk's exclamation, those in the special seats also began to murmur and converse with each other.

"The Heavenly Demon-Subduing Palm of Brahma the Tathāgata! That is indeed……!"

"How could a Shaolin's secret technique be in that child's possession……"

However, regardless of what others said, the most surprised and bewildered individuals were the martial monks of Shaolin Temple themselves. After all, it was like seeing a family heirloom that was thought to have been burnt and lost due to their ancestor's mistake, shining brightly in someone else's hands.

Weifeng retreated one step, two steps, three steps…… Finally, after retreating five steps, he managed to dissipate the True Qi that shook his meridians.

In contrast, Qing stood still, simply extending her palm forward.

Everyone watching could see the outcome of the clash from their contrasting reactions.

Weifeng had learned all 72 secret arts of Shaolin and had been taught all sorts of Divine Arts. In terms of variety, he was like a walking scripture storage (Shaolin's library).

However, since he learned widely but not deeply, his mastery of each was not high, so even the peerless Divine Art like the Hundred Steps Divine Fist was still not fully mature.

But for Qing, although it was a trick that she had learned overnight, she knew how to use all the moves of the 12 Constellations correctly, so the outcome was as it was.

Weifeng closed his eyes and inhaled deeply, hwooooooop, for an extended period. Qing watched this unfold.

If it had been my Middle Number Technique, I would have just blown him away. But since it was a striking technique, he's enduring it again.

Still, it was clear that he had suffered a great shock, so she waited for him to recover.

After all, a contest was not a life-or-death struggle.

Finally, Weifeng exhaled as much as he had inhaled, hwooooo.

With the mighty Buddhist palm strike, his body trembled. His internal organs ached and every joint was in pain. But his mind was clear, as if it had been cleansed.

"Amitabha. This monk has shown a disgraceful appearance. Benefactor is-"

Weifeng started to speak but stopped.

It was the sad fate of a man who had encountered Qing's harmful, bare face, from which the veil had been removed.

\textit{What, Mara? Is this the temptation of Mara……!}

Moreover, Weifeng had never left the mountain since entering Shaolin at the age of five. As such, in his twenty-two years, he had never seen a woman, let alone touched one.

In fact, he was not even allowed to go out until he won the contest. So, when he was told not to look at Qing's face, he had simply treated her like any other martial artist.

But now?

Weifeng, who had no immunity to women, suddenly encountered a beautiful woman of such heavenly beauty. His chest pounded, his composed mind wavered and churned, and his Yang energy surged, making it hard for him to even stand properly.

Qing pondered for a moment. What is this? Is he trying to anger me? What's the best way to make someone angry?

But the contest was not over yet, so Qing stomped on the floor of the contest arena and advanced.

Qing's fist extended. And then, thwack, Weifeng was struck on the side and stumbled backward. Qing's fist extended again and again, thud! Thwack, thud. Bonk!

Where had his previous momentum gone? Weifeng was busy blocking and parrying, constantly retreating.

Not only was his counterattack non-existent, but his stance was also awkward and unstable. Moreover, he did not meet her gaze, looking up or down or far away. Even when his focus neared, it was on her forehead or the tip of her nose, never meeting her eyes.

Qing's eye twitched.

\textit{Is this bastard playing games with me until the end?}

Qing's hand soared high.

Thwack!!!

A crisp sound resonated.

It was the sound of her open palm striking Weifeng's bald head.

Soon, there would be a clear handprint on his bald head, not the hand of Buddha.

Weifeng wrapped his hand around his forehead-head and stumbled backward.

Qing raised her voice.

"Monk. What are you doing right now? Why aren't you fighting properly?"

"I-It's just that. Mmm, this monk, this monk forfeits."

The arena, which had been quite noisy, fell silent.

"Mm. With the opponent's forfeit, the winner-"

"Just a moment."

Qing interrupted the judge declaring the outcome.

"Monk Weifeng. Can you please clarify? You're not conceding defeat, nor are you admitting defeat, but you're forfeiting?"

"But, Benefactor. Isn't it impossible to determine a winner in this situation?"

"It is impossible to determine a winner in this situation? Why is that? Did your Inner Qi run out? If so, shouldn't you declare defeat, not forfeit?"

"That is not the case! It is just, how could this monk possibly, with a Benefactor like you."

"What about me?"

Qing's voice turned sharp.

Then, Weifeng exclaimed in a voice full of injustice.

"Sorcery! It is sorcery! Like an avatar of Mara, no, Mara itself! How could this possibly be, Amitabha, Amitabha……"

"……?"

A deep furrow formed between Qing's eyebrows.

"Sorcery? Are you saying I did something, using such immoral words?"

"How can a fair contest be possible in this situation! With such a beautiful appearance and allure, it is sorcery, is it not! Moreover, how could this monk possibly attack such a frail woman!?"

At that, the audience collectively lost their words.

The words of the Shaolin monk, who had been launching fierce attacks as if to destroy the contest arena, were quite peculiar.

"Are you saying that you had no qualms about striking the chest and face of an ugly woman, but suddenly a beautiful woman becomes too frail to touch just because of her appearance, despite being the same woman?"

"Th-That is……"

The Great Master could not bear to watch any longer and covered his face.

Because Qing asked that, Weifeng ended up saying that it was okay to hit ugly women, but not beautiful ones.

Even if a man of the world were to say such a thing, he should not be so forthright. Moreover, it was absolutely not something a Buddhist disciple should say. What was the point of the physical body when it was just a vessel when facing the saha world?

Ximen Surin thought to herself, My disciple has a good point there. She's good at putting someone in their place!

In reality, people would treat women with ugly or plump appearances harshly, hitting, pushing, and cursing them, while being overly kind to beautiful women, as if they would give up their liver and gallbladders for them.

The spectators, who were watching, were in deep agreement with Weifeng's opinion. They, too, thought it was okay to beat up ugly women.

However, aside from that, the fact that he had been beating her up so hard and was now calling it sorcery was honestly quite pathetic. It was very, very pathetic.

Meanwhile, in the contest area, when everyone was jokingly shouting for the Ugly Swordswoman, there was one section that remained unusually quiet and reserved.

It wasn't because they were particularly well-mannered or enlightened by chance.

It was just that whenever someone uttered the word 'ugly', a group of people would glare at them while fiddling with their weapons, clearly indicating their intention to kill if they spoke even one more word.

The Ronins nodded in satisfaction.

Young Lady Ximen's beauty was truly worthy of being called the best under heaven, so it was only natural that even a Shaolin monk could not maintain his composure.

While the ship contest arena was gradually quieting down, the judge in charge eventually stepped in.

"Haaaa…Weifeng, how much of your Inner Qi remains? You used Force Compression quite a lot, so it must be almost depleted. Is it more than 10%?"

"That is…It is not."

"What about you, Young Lady Ximen?"

"I haven't even emptied half of it yet."

"You still have that much remaining?"

"Yes. Would you like to check my pulse and confirm?"

Qing offered her wrist politely.

The judge shook his head. Wasn't asking to check more than enough proof?

"Considering the consumption of their respective Inner Qi, it is clear who would have won if the match had continued normally. Therefore, I declare the winner to be Young Lady Ximen of the Divine Maiden Sect!"