\chapter{The Appearance of the Divine Dragon (3)}

Qing thought to herself after tasting the essence of martial arts, which
was said to be from the Shaolin Sect, the greatest under Heaven.

Ah, this is so dirty. So dirty.

They're all just martial artists who specialize in fighting, huh.

If I just say that it won't work even if I keep getting hit by a sword,
then it's all over, right?

This is just a field tilted to an extreme degree, no, it's not even a field, it's
like having a fortress built on a wall and then having a siege battle on
it……

If these were real swords, then I'm sure I could have stripped off their
skin, even if I can't do anything about the muscles. Then, I could have
made them bleed all over. If I skinned them and dug in, then they would
have cried from the pain, whether they were a Shaolin Monk or
whatever.

But the Wulin Tournament was an event for fellowship, not a place to
start the cycle of hatred by looking for new enemies.

So, it's dirty, but…

I need to find a method.

Qing briefly reviewed the contents of the match.

Distance. Yes, the distance is tricky.

Beyond martial arts, the importance of distance in the broader category
of fighting was the act of fighting itself, which did not need to be
emphasized.

In fact, a longsword was more powerful than a sword, and a guandao
was more powerful than a longsword. That was because longer blades
allowed one to attack unilaterally from a distance where the opponent
could not reach.

Of course, long weapons had larger movements, so once someone got
close, they were quickly neutralized.

However, if one were to fight with exactly the same skills and
conditions, they would likely suffer a fatal injury before they could even
get close to a long-armed martial artist, so larger, longer weapons
actually had more destructive power.

But when the authorities held absolute power, such 'deadly weapons'
were illegal for individuals to carry, so swords became the mainstream
choice for martial artists.

It was a weapon with a perfect balance that fulfilled everything from a
moderate length, moderate weight, moderately long range, and
moderately short range. For that reason, the sword was called the King
of All Weapons and was the most preferred armament by martial artists.
Other options included the dao, which was similar to the sword but had
only one edge, or the short spear, which could be joined together to
transform into a long spear or a guandao.

Or there was the staff, which boasted an innovative functional beauty
as a weapon and a walking stick in one.

Speaking of functional beauty, the axe should not be left out, with its
wood-cutting ability to procure firewood (live trees) at any time.

However, those who were too poor to afford weapons, or those who
were slightly less intelligent, chose not to use weapons.

They were the ones called by the derogatory term, martial artists.

In Qing's hometown, renowned fighters would say in unison that one
should not fight but run away when facing a person wielding a knife.

To these martial artists, distance meant nothing except being so close
that they could share each other's breaths.

And then, they had the audacity to say that in such a close proximity, no
weapon could defeat a martial artist.

It was nonsense to make such an impossible assumption when they
couldn't even get close enough to penetrate the opponent's weapon in
the first place.

However, the Shaolin had overcome this beautifully.

They had enhanced their resistance to weapons with all sorts of
external training, such as the Iron Robe, Iron Broom, Golden Bell
Canopy, Shooting Star, Iron Knee, Friction, Finger Drills \footnote{literal
translation from 拔釘, meaning 'to pull out nails', but it didn't seem to
it}, and the Immortal's Palm, even if it wasn't to the level of the
Indestructible Diamond Body.

Due to this rigorous training from a young age, the martial monks of
Shaolin inevitably aged faster on the outside.

Then, Qing suddenly had a great realization.

Ah. That's right.

It wasn't a matter of principles like softness or hardness.

From the start, the problem was trying to seriously converse about
martial arts with such an idiotic martial artist.

What kind of martial art is that?

Qing sheathed her sword.

At that, Wolbong asked in puzzlement.

"Almsgiver? Are you forfeiting?"

"No. Now I'm going to get serious."

At the same time, Qing took a stance.

It was a peculiar stance where she looked at the opponent obliquely,
with one lightly clenched fist in front and the other fist positioned in
front of her solar plexus.

Yes. Koreans gotta stick with Taekwondo, of course.

If he's playing around in a sacred match, then there's no reason for me
to be serious, right?

"Then, here I go."

With that, Qing dashed forward.

And then, she stomped three steps at close range, extending her fist
with force. It was a straight punch without any technique, to which
Wolbong responded with a straight punch of his own.

Bang! It was an unbelievable sound for a collision between two fists.

The power of Sword Force was in its destructive force, as if wrapped in
steel, not in its sharpness.

And the lower part of Qing's elbow was practically in a state of
Indestructible Diamond Body, though it was just a knockoff version
called White Hand, so she could withstand an attack like Sword Force
just fine.

Agh. That hurts like hell, though.

Pain was inevitable, however.

But Wolbong's expression turned serious, as he had never imagined
such a powerful force.

Qing extended her tingling fist once again.

Wolbong's forearm pushed Qing's fist outward, and his other arm
drifted away. It was a fist rushing towards her side. Qing spread her
palm to block Wolbong's fist.

And then, the brawl began.

Their fists delected each other, and then fists collided, sometimes
meeting palm blades and slicing through the air with the elbow while
the knee soared and crossed.

Excluding the Seventy-Two Arts, Wolbong was a master who had
learned the most powerful martial arts of Nahan Fist and White Lotus
Divine Fist.

It was incomparable to Qing's crude imitation of martial arts, which
only resembled the form of the original.

However, the fight between the two was surprisingly even, going back
and forth like a seesaw in a display of intense struggle.

This was because Qing was a woman.

In fact, Wolbong was also harboring complaints about the unfairness of
the match.

After all, there were certain areas he was not allowed to hit when
sparring against a female martial artist.

At best, it was the limbs, shoulders, and torso, which were not fatal
and quite sturdy. Moreover, even if he aimed at the torso, it was only
above the navel.

On top of that, Qing had an absolute defense against attacks to her
solar plexus, the most fatal weak point of the torso.

In contrast, Qing was freely aiming for Wolbong's head, including his
jaw and the area around his eyes.

Wolbong's dissatisfaction was steadily growing.

Qing's hands, which had been delivering powerful straight punches with
sharp angles, suddenly drew a soft yet peculiar curve and grabbed
Wolbong's forearm.

Qing could lift two hundred geun with one hand. And that was just
pure arm strength without using any momentum.

With both hands, it was four hundred geun.

But when using all the muscles in her body, she could exert
overwhelming strength, worthy of the title of the female version of
Xiang Yu, who was known to have been able to lift a mountain.

Wolbong's body levitated. Bang!! With a loud noise, Wolbong's body,
which had drawn a semi-circle, violently collided with the floor of the
stage.

Even in the midst of this, he managed to lessen the impact by using a
breakfall technique, which was a testament to the rigorous training of
the Shaolin.

However, Qing's hand was still firmly grasping Wolbong's wrist.

Wolbong flew. Although it was a very short light, just rising and
drawing a semicircle before crashing, it was still an amazing miracle
that made the audience of the match gape in awe.

Bang! Bang! Bang! Bang! The continuous heavy impacts made the
audience fear for his life, even as they couldn't take their eyes off the
spectacle.

It was when Qing was determinedly swinging Wolbong around.

Suddenly, Sword Force shot up from Wolbong's fist and struck his own
wrist like a hammer.

"Argh!"

Qing screamed as she was struck by the Sword Force.

If she took a few more hits, her bones would not only be damaged but
also shattered.

Wolbong's fist clenched again. Qing released Wolbong's arm just before
the trajectory of the Sword Force struck.

"Kugh."

Wolbong, who had struck his own wrist with his own Sword Force,
groaned and rapidly retreated. But it was only for a moment, as he
regained his balance with the Thousand Pounds Drop technique and
stood, hands clasped together.

"Whew. Whew."

Qing caught her breath.

Swinging around a person who was desperately resisting required a
completely different level of strength compared to swinging an iron
ball of the same weight.

It was then. Wolbong suddenly extended his fist, causing Qing to
instinctively try to step back–

Qing flew a zhang away and tumbled to the ground. Ahhh, fuck, why,
why the chest again! This fucking bastard! He's aiming for my chest
now, even in a match!

And then, a shadow suddenly loomed over her.

Qing hurriedly rolled on the ground, dodging the bald head that had
blocked the sun.

Qing, having mastered the art of rolling on her bed through countless
practices, was a professional tumbler who had reached the level of a
master in the technique called Naryeotagon.

A fist, as if trying to snatch a bird, pierced through the floor of the
stage. Qing's mind, even in the midst of a world spinning around, did
not miss that brief moment, and her heart sank.

Wasn't that a match? Isn't that a move to kill someone?

Having rolled away, Qing quickly got up and saw Wolbong's eyes, which
were filled with killing intent. He had the eyes of someone who was
truly pissed.

"Whewwww. This lowly monk seems to have underestimated Almsgiver
far too much. Now, I will no longer hold back and will do my best."

"Ha."

Qing snorted, finding it absurd.

What? Why is he getting angry?

The one who was being toyed with in this sacred match was Wolbong,
not Qing.

Until now, he hadn't used any of the real Shaolin Divine Arts, except for
one move of the Hundred Steps Divine Fist as a warning. It was as if he
was hiding his Sword Force.

There was a limit to how much one could look down on another, and
this was why Qing had become angry and pushed him around with just
pure strength, rather than martial arts.

As he had said he would no longer hold back, Wolbong took a step
forward. In an instant, Wolbong's form multiplied and rushed in.
Qing focused her vision to catch the incoming attacks and tried to grab
him to throw him down again.

Suddenly, five steps away, a palm extended, and a massive palm print
made of Sword Force struck.

It was the Geat Golden Dragon's Hand of the Powerful Vajra Palm.

Qing urgently stepped, her form splitting into eight as she performed
various actions. She leaped into the air like a crane, gracefully spun
backwards, dashed forward as if sliding on the ground, bounced away
with both feet, ran nimbly on all fours like a beast, quickly spun
vertically after executing an Iron-Bridge, slowly walked in place, and
shot forward like a cannonball, each in eight directions, before suddenly
disappearing four steps away.

Qing, having used the emergency escape technique of the Ethereal
Steps, turned around as a matter of course.

Then, once again, she saw the multiple shining bald heads of Wolbong,
leaving behind afterimages as he approached.

All sorts of supreme techniques poured out from Wolbong's hands.

The Nahan Divine Fist, which seemed to leave afterimages as if it had
six arms, the White Lotus Divine Fist, which boasted a destructive
power said to shatter cliffs, the Great Golden Dragon's Hand, with its
Sword Force swirling around, cutting through anything it touched, and
the four streams of Sword Force that flew in a curve, which was a
Divine Art called the Finger Bullet.

Qing was busy dodging, blocking, and deflecting the attacks with her
arms and legs, as well as rolling, crawling, leaping, and flying.
Seriously, what the hell. What the fuck is this?

It was only now that Qing realized the full extent of the saying, 'All
martial arts originate from Shaolin'.

However, Qing's eyes were simply fierce.

He thinks he's so great just because he's a Transcendent Realm Master?

As if someone who is not short on Inner Qi would be intimidated by
such attacks.

If he keeps spamming Sword Force like that, even if he ate all the
Shaolin Elixirs, like the Great Revitalizing Pill, as a substitute for
meals, he won't last long.

And then, Thud!

Qing's body staggered greatly after being struck on the outside of the
knee.

This, you fucker! It's foul to kick, you know!

Of course, this was a supreme technique among leg techniques, called
the Peerless Kick.

A fist next to the bald head was caught in Qing's tilted gaze. Qing
urgently raised her forearm, and, Thud!!

Qing's form split again.

After turning around, Qing landed and spat out the blood that had
filled her mouth.

The punch aimed at her cheek was blocked, but she ended up hitting
herself in the face with her own palm, tearing the inside of her cheek
and turning her mouth into a mess that tasted like metal.

"Alright, you hit me, didn't you……!"

With her eyes bloodshot, Qing rushed forward with all her might. As
the audience blinked, the distance of four zhang narrowed in an
instant, causing them to tense their eyes in surprise.

Wolbong calmly pulled back his fist from his position.

It was the preparation for the Hundred Steps Divine Fist.

Finally, advancing one step forward with a presence as massive as a
mountain, just as he extended his fist-

Qing also reached arm's length and stretched out her palm as if she
would not back down.

In the moment the fist and palm collided…

BOOOOOOOOM-!!!

Suddenly, a deafening roar shook the heavens and the earth, and a
fierce explosion of True Qi swept through the audience, causing a
violent wind to blow past.

And a single veil, fluttering in the rough wind, soared into the sky.