\chapter{The Appearance of the Divine Dragon (9)}

The Heaven-Shattering Demonic Qi was smiling.

The pure, orthodox Inner Qis of Buddhism and Daoism, bustling within
the dantian, were nothing more than beings with fleeting, mortal fates
to the Heaven-Shattering Demonic Qi.

The Heaven-Shattering Demonic Qi was the very essence of Angra
Mainyu, the Ahriman. This was the God of Destruction that the
Heavenly Demon Divine Cult spoke of, the foretold apocalypse that
would bring down a giant star to annihilate everything for the sake of
the world's recreation.

As such, the Heaven-Shattering Demonic Qi simply sat still, observing
haughtily.

No matter how much those feeble True Qis of mortals raged, once the
flesh died, they would scatter and return to nature.

Then, the only Qi that would remain in the end, the strongest True Qi,
would be the Heaven-Shattering Demonic Qi, immortal until the
foretold future.

The Heaven-Shattering Demonic Qi simply rested for a moment,
indulging the excitement of the short-lived beings, watching their
childish antics……

Thump! Thump!

Today, too, the Blissful True Qi, which was pounding on the hideous
Demonic Qi that was firmly stuck in a corner of the dantian, tilted its
head.

What the? Why is this bastard smiling?

The Heaven-Shattering Demonic Qi was an utterly bizarre and
heterogeneous Demonic Qi.

The Imagery of ordinary Demonic Qis was utterly wicked, always
whispering to their owners and inciting them to be cruel, lewd, and
heartless.

However, the Imagery of the Heaven-Shattering Demonic Qi contained
only destruction, so if one was to peek into its contents while it was
being diligently hammered, it was a pure destruction that even held a
sacred longing for a new creation.

The Blissful Maiden True Qi, which had been pounding on the Heaven Shattering Demonic Qi that was hardened like a rock, could not find
any enjoyment from it today, just like every other day.

So, it whipped its gaze around in search of amusement.

As if pretending not to look, the Demonic Qis under the command of
the Violet Lightning Demonic Qi, who had been crouching in the
corner, were stealthily taking steps towards the exit leading out of the
dantian.

'That crazy True Qi is gonna start beating our asses again while chasing after us', they thought.

The Blissful Maiden True Qi watched the scene quietly, as if to say 'Go ahead and try to escape if you can'.

Then, it stomped one foot down! Startled, the Demonic Qis kicked at
the exit of the dantian-

-only for the door to suddenly swing inwards, smacking them right in
the face, causing them to roll back into the dantian.

And upon a palanquin carried by a dragon and an elephant, a new guest
appeared!

The dragon and the elephant were considered the most auspicious
animals in Indian Buddhism, which was why a golden dragon and a
golden elephant, shining brightly in gold, were never absent from
Indian Buddhist art.

The Great Purity Zen Qi squinted its eyes, uncertain.

The atmosphere seems like it's one of the Buddhist family, but why
has it come covered in so much flashy and secular dirt?

However, the Yijin True Qi, which had originated from the teachings of India, felt a familiar scent of its
homeland.

Thus, the Yijin True Qi enthusiastically embraced its fellow True Qi from the same hometown.

Only then did the Daoist True Qis watch their reunion with the warm
smiles of a father/mother.

At that, the Violet Lightning Demonic Qi, which seemed to say 'Fuck
this. I can't watch this any longer', dashed out of the dantian, with the
other Demonic Qis following after it.

And the mold stuck to the wall, the Heaven-Shattering Demonic Qi, just
kept smiling. For some reason, tears were flowing, though.

The Heaven-Shattering Demonic Qi was smiling……

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

I thought I should talk to Gong Sonye if she ever showed up, but according
to Nannah, she was busy participating in family events.

"She just stands there at every banquet with an expression that says she
doesn't know what to do. Well, either the Gongson or the Sima Clan will
ascend to fill the empty seat of the Ten Noble Clans, so it's time for
them to go around and greet everyone."

"Mm. I see. Ah. Right. Nannah. If one uses Innate True Qi, can it be
replenished with something else?"

"What!? You're going to use Innate True Qi in that state? If you do that,
I'm really not going to see you anymore, Qing'ah. I won't see you."

Dang Nannah firmly put her foot down.

"No, it's not me. I mean, what if there's a martial art like that."

"Ah. That kind? Well, it depends on the martial art, but usually, one
mixes a bit of Innate True Qi with their True Qi. Doing so makes the
low of True Qi explosively faster. Of course, the capillaries will also
gradually get damaged. Just like how someone's swollen tits burst all
their blood vessels."

It seemed like she still had some resentment left.

"I said I'm sorry. So, if you rest well or take some elixirs, will the Innate
True Qi be replenished? Like a Grand Rejuvenation Pill or something."

"You don't need to go as far as a Grand Rejuvenation Pill. Any well devised Elixir Pill will have the effect of replenishing Innate True Qi.
But, using it in the first place is, how should I put it? Ah, right……"

Innate True Qi was not originally created to be used like that. It was the
very fuel that naturally sustained a person's life, like a beating heart or
breathing.

That was why it formed a coil around the heart, the center of the body,
and was also called the Middle Dantian.

But if one kept using it, the force that prevented the Middle Dantian
from leaking would weaken. In other words, it was like the door
becoming loose.

"A newly fitted door won't let in even a single gust of wind. But as you
keep opening and closing it, it can get a bit twisted and small scratches
and holes can appear on the paper covering."

"Can't the door be fixed?"

"You can't really fix it. Maybe during Overhaul Rebirth? Or perhaps at
the Profound Realm. Starting from the Profound Realm, the body
repairs damaged parts on its own and regrows new flesh on old
bodies."

It was a phenomenon known as Reversal of Aging.

"Mm. Then, it seems quite bad, doesn't it?"

"Is that all you have to say? It's only better than dying, but that doesn't
mean you should learn just any random thing. After all, once a person
has something, they'll want to use it, so it's better not to learn such
martial arts in the first place. Just take a Numinous Seizure Pill, ah.
Right. Here, take this."

Dang Nannah thrust out a wooden box she had taken out from her
bosom.

"It's a Bursting Qi Rapid Tendon Pill. It only lasts for about two hours,
so use it to escape when you're in danger."

"Oh. Thank you. I keep receiving things from you."

"Mm? Mmm. Hehe. If you're grateful, don't just say it with words……
Argh, seriously, to think you got hurt at a time like this. Consider this
debt. I'll collect it all later."

"Debt? What are you going to collect? I'm your benefactor, you know?
What do you mean by debt? Are you going to act like some sort of
loan shark or something?"

"Urk."

Dang Nannah's face crumpled in frustration.

"It was a joke. I'm always grateful. For always taking care of me."

When Qing said that with a gentle smile, Dang Nannah's expression
became dazed in an instant, her mouth agape.

"Argh, seriously, you're driving me crazy……"

"Hm?"

"Nothing! Anyway, I'm going now, okay? I suddenly remembered
something urgent. Mm. I think I left a decoction on the fire. See you
later, then!"

Then, as the sun set, casting a crimson glow, she vanished in an
instant.

Qing scratched the air once with the hand she had tried to use to stop
her.

"Hm. I was going to ask if she wanted to go to the Nameless Temple
together……"

Well, whatever. I'll just go alone.

Qing walked on, clink clank, clunk clunk.

She was on her way to deliver a copy of the Buddha's Palm to the
Nameless Temple.

The Nameless Temple's original name was the Cheonjeong Temple,
known as one of the four great temples of the Northern Song Dynasty.

It was even said that a nine-story Sarira Pagoda was erected high into
the sky, showcasing its grandeur.

Unfortunately, it was all washed away by a flood. This was the basic
reason why temples and Daoist monasteries were located high in the
mountains.

Thus, sediment accumulated, and another temple was built on top of it,
only to be swept away by another flood. Then, more sediment
accumulated on top of that……

This cycle repeated until the nine-story pagoda was left with only three
stories above ground. After several temples were buried layer by layer
underneath, the area was considered an ominous land and was
abandoned for a long time.

That was why this place was now called the Nameless Temple, and the
Sarira Pagoda with only three stories remaining was one of the two
pagodas of Kaifeng, the Beon Pagoda.

But why is everyone staring at me?

Is there a spectacle somewhere?

After all, the famous Veiled Lady was walking around, shaking her
enormous butt that far exceeded the average of Zhongyuan.

It was a given that men could not take their eyes off her once their gaze
fell on her, as if possessed by her alluring figure.

If this wasn't a spectacle, then there was nothing much else worth
seeing in the world.

But then, it seemed like she could hear the sound of wooden blocks
clacking together, as well as the sound of coins clinking.

Thus, Qing walked past a group of men who were suddenly reciting
sutras while standing awkwardly in the middle of the street, unable to
go one way or the other, and arrived at the Nameless Temple in the
corner of Kaifeng.

When Qing first came to Kaifeng, she had once visited to see the
famous two pagodas.

Back then, it was a desolate ruin, but after the Shaolin monks roughly
repaired it and started burning incense, it somehow had the appearance
and smell of a temple.

When Qing set foot in the Nameless Temple, an old monk wearing the
yellow-orange robes of Shaolin emerged and greeted her.

"Amitabha. Young Lady Ximen, you have come."

"Yes. Is Great Master Wunue inside?"

"He said he would be away for three or four days. Great Master is
occasionally wrong, as well. He is currently overseeing the disciples in
the Great Hero Hall."

"Ah. Yes. Well then."

"Wait. Mm. But the Great Hero Hall is currently full of martial monks
undergoing training. If they see you, they will all be possessed by
demons. How about waiting in that room over there? I will call him right
away. By the way, it seems like you have completed the scripture, I
presume?"

"Yes. Ah. Shall I give it to you now? If Great Master Wunue is busy,
there is no need for me to take up his time by personally delivering it."

At that, the old monk smiled benevolently.

"How could that be? How can a nameless monk like me dare to receive
such a great task? Come, please wait here."

Since the nameless monk said so, Qing followed his instructions
obediently.

But when the monk turned and caught a glimpse of her from behind, he nearly choked.

This monk — Abbot Wolhyeon, the head of Shaolin Temple — thought in a mild panic:

What in the world is with that walk?! If the Arhats see her, we’ll be scraping fallen blossoms off the walls by morning!

Qing didn’t have to wait long.

As soon as the news was delivered, Wunue left the Arhats and dashed over.

Wunue's expression was quite sullen.

"Hmph. To think you'd write the entire scripture in just one day? You
were told to write each letter with utmost sincerity and care since it
was going to be left for generations, weren't you?"

"Eyyy. I wrote it very neatly. You'll be surprised when you see my
handwriting. Even a scholar from the Imperial Academy could not help
but admire my penmanship."

"Hmph. You wrote it quickly and sloppily in just one day. Let me s……"

As Wunue held up the book, his words stopped abruptly.

He didn't even open it; he just stared at the four characters written on
the cover, 'Buddha's Palm', and froze.

What is this! What is this writing that reaches for the sky with such
vigorous spirit, yet stands tall like a great mountain?!

It was truly a masterpiece, a treasure that everyone would try to
obtain even if they had to pay a thousand gold!

The Immovable Mind of Shaolin was unshakable, like a mountain.

Thus, Shaolin's writing also strived to resemble a mountain.

However, now that he realized it, all the pride he felt in the signboards
of Shaolin was in vain.

There was a true mountain itself in this writing, so they had just been
boasting about the highness of a mere hill.

If only all the signboards of Shaolin could be replaced with this
writing, it would truly be a phrase befitting of Shaolin, the great
northern mountain of mountains……

"Hut! Amitabha! Hoho……"

"Ah, why are you doing this?"

"It is nothing. Hooo. I am dizzy. I thought I had already severed all
desires, but I am still far from it. I am but a mere mortal……"

Realizing his own greed, Wunue muttered in vain.

How could such excellent handwriting make even the greatest monk
of the largest temple under heaven so covetous?

"Is this truly your handwriting?"

"Yes. Isn't it well-written?"

"Well-written and whatnot… Mm. But how could you have completed
such a thing in just one day? Hm. The inside must be written sloppily."

As Wunue hastily flipped through the book, he froze once again. 