\chapter{The Appearance of the Divine Dragon (7)}

After the sparring matches ended, Qing soaked in the Medicinal
Herb Spring in the evening to absorb the medicinal properties and then
lay down on the Oil-Refined Training Platform.

And after three grueling hours of precise torture, Chunyu Hak
collapsed on the floor, leaving Qing to fend for herself.

As Qing, still bound, regained control of her body, she thought.

Ugh, every inch of my body aches. Just how much did I struggle to
make it this bad?

Her joints and tendons were obviously sore from being intentionally
worked to the brink of disrepair, but the full-body muscle aches and
spasms were the result of her desperate attempts to escape the
process of oil-refined training.

This damn mental parasite, going on and on about being the
Heavenly Demon Supreme or whatever, was actually so fucking weak
and soft.

To think he would cause such a fuss after a mere three hours of joint
dislocation and bone misalignment. Ah, it hurts so much.

If the mental parasite had known, he would have felt wronged, but the
vicious avenger who had plunged the world into misery four times
during the four Great Demonic Wars was now just a broken spirit,
destroyed by pain.

Qing thought it was a bit much to be asking to be killed after just a
year of suffering, especially since he was the one who turned the
Heavenly Demon Divine Cult into the Demonic Cult.

After the rewarding oil-refined training session, she went to sleep and
woke up to find the sun high in the sky.

Wondering who was there, she went down and saw, oh?

"Well, if it isn't you. Eugeugeu. Why isn't there a
mountain when I come up? Mountain! When can we have a proper
fight?!"

"Hmph."

"What? Was it not this mountain? San, which mountain did you climb
that you're not visible? Haha, looks like you're still far off."

"……Try to keep it to a minimum."

"Hmm. It seems like Ye was stronger than I thought."

"That woman."

Sanie's expression hardened.

Qing frowned along with him.

"What do you mean, that woman? Why don't you try being a bit friendlier?
She's really nice, despite being a bit shy."

"It's not that. Hmm."

Peng Daesan wiggled his eyebrows, then went 'hmm' again, and then
wiggled his eyebrows some more. It seemed like he was deeply conflicted
whether to say something.

So, Qing just asked.

"What is it?"

"I'm not sure if I should tell you this."

"What is it? If you've started talking, you have to finish. You want to
see me frustrated to death?"

"Hmm. Let me preface this by saying it's not an excuse. I just think you
should know."

"What is it that you're being so grandiose about?"

"She used Innate True Qi. It seems she has learned some special martial
art of that nature."

"Who? Ye?"

Sanie nodded in response.

"Huh. She uses Innate True Qi? She's using up her lifespan to use
martial arts?"

Qing understood why he said it wasn't an excuse.

It was to tell her not to think that Gong Sonyay had resorted to using
Innate True Qi just to win the sparring match.

Though, from what Qing heard, it seemed like there were indeed such
intentions.

"You should know this. I lost without any hard feelings, so don't look at
me with such impure eyes."

Peng Daesan emphasized once again after seeing Qing's suspicious
gaze.

Qing said with a serious expression.

"Hmm. I should have a word with Ye."

Why on earth would someone risk their life, or rather, consume their
lifespan, just to win a sparring match?

Was she that desperate to win the Sparring Meet?

Compared to that, I'm………

As Qing fell into deep thought…

"Unni! Gaga-unni!"

"Oing. This voice. Where are you!"

With a pitter-patter of small feet, something wrapped itself around
Qing's pelvis.

"You rascal! Hyang-ie!"

Qing lifted Je Galyang in one swift motion and spun her around in
circles……

"Kyahahaha!"

Not knowing dizziness, Je Galyang burst into the clear, innocent
laughter typical of children.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

They were on their way to the Martial Arts Hall.

But well, how should I bring this up? It's a bit awkward to just ask for
your Buddha's Palm, isn't it?

Moreover, Ximen Surin's nagging would surely be nothing to scoff at.

As such, their steps towards the Martial Arts Hall slowed, making them
seem like a leisurely stroller.

Upon reaching the Martial Arts Hall, they saw young, vigorous youths
focusing on their sparring, sweating on this fine day.

How wonderful this time is, they thought, as they looked for Qing's
figure. It wasn't hard to find her, since her beauty stood out.

She was sitting comfortably on the grass with a small girl in her arms.

'Gaga-unni', she says? What a curious nickname.

The Great Master Wunue tilted his head.

Then, he thought, well, women can call each other whatever they want
when they're close.

"Cough."

"Ah."

Only then did Qing notice Wunue.

Amidst the wind, her five senses were sharp, yet she hadn't noticed
him. She was momentarily alarmed, but upon seeing the shiny,
gleaming bald head, she quickly relaxed.

"This old man is Wunue, a mere monk. You must have heard of my name,
yes?"

"Ah! The Greatest Under Heaven! Hello. This girl is called Je Galyang."

Je Galyang, who didn't even count to three before blurting out, caused
Qing to miss her timing.

What? Isn't it the law of this land to shout after
two beats?

Qing also stood up and politely greeted him.

Then, Wunue finally got a closer look at Qing's eyes.

The sinister madness that lurked behind the clear brilliance of the
Daoist and Buddhist auras, madness………

\textit{Th-This, this mad dog!}

\textit{How could you pick up and raise the Heavenly Slaughter?!}

If it were other Masters, they would have thought that the madness
was inherited from the Female Mad Dog's teaching, but the eyes of the
Greatest Under Heaven could see through to the essence.

The most ominous starlight in the world was being crushed and
firmly held between two hands.

One hand was the pure and clear path of Daoism, and the other was the
great benevolence and compassion of Buddhism. It was as if the Dao of
the world was barely holding onto the most sinister of natures.

"Hoho. Hmm. This old man has something to discuss with this child, but
would the little lady of the Zhuge family step aside for a moment?"

"Ah. Yes………"

Zhuge Xiang bowed and then, turning her head repeatedly, ran towards
her older brother.

"Hmm. Indeed. I have something to discuss with you, so why don't we
change our location?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Martial Arts Hall also had a tea room. After sitting down and
waiting for the attendant to bring tea, Wunue maintained a serious
expression and remained silent.

So, Qing spoke first.

"Great Master. Did you come because of the Divine Arts? I should have
visited you first. I apologize."

"Hmm. No. It's not a big deal for the person with business to come
first. It's just that, well, since an elder should order around the younger
ones, hmm, well, I guess as an elder, I should order them around."

The Great Master Wunue spoke as such and looked at Qing.

The ominous star that would plunge the world into chaos was right
before his eyes.

\textit{That fucking Ximen bitch kept singing about women's rights
or whatever, but this is truly crossing the line.}

\textit{No matter how much she suppressed the Heavenly Slaughter with her
cultivation, how could a human being possibly defy their destiny?}

\textit{Eventually, she would become a great evil, a calamity that would make
blood flow like tears.} 

\textit{In that case, I should end her life here.}

\textit{The Buddha's Palm and whatnot, that was not what was important
right now-}

"So, should I recite the verses now? Or I can write down the Secret
Manual for you."

"Huh? You're just going to give me the Divine Arts?"

"More like returning it, you see? Since it was originally from the Shaolin
Temple, it's only right to return it to its owner."

"…Was that your thought, or Surin, no, your master's thought?"

"My master said it wasn't her fated connection and told me to do as I pleased."

There was not a hint of hesitation in her expression, indicating that
she was speaking the honest truth.

The Great Master Wunue's mind was blown.

"If you wish, I can give you all the wealth of the Shaolin Temple. What
do you say? Would you still just hand it over?"

"Eyy. What would a Daoist do with all that wealth? It's not like the
Divine Maiden Sect is poor, and I don't really need money for myself."

"Hoho. Then, what about elixirs? You must know the value of the Great
Revival Pill, don't you? There are twelve of those in the Medicinal
Herb Hall right now and over fifty Lesser Revival Pills, all of which I can
give to you."

"Hmm. My master said that my Inner Qi is already comparable to that of
a master of the Unrestrained Realm, so I don't really need elixirs. Ah.
But if you could give me one or two, that would be nice."

"Why two?"

"One for my master. And one for, uh, a friend who uses a martial art
that consumes their lifespan."

"You mean the child from the Gongson family."

"Ah! You knew?"

"The Xuanyuan Sword is the sword of the Yellow Emperor. How could
there be no price for a human to wield the sword of an emperor, no
matter how high their realm?"

Here, the Yellow Emperor did not refer to a mortal ruler.

Originally, the term 'Yellow Emperor' referred to a god, as the people of
Qing's homeland would put it.

How could a mortal dare to wield the power of a god without paying a
price?

It doesn't seem like a very high-grade item, considering it's gold.

Qing thought as such.

But she didn't realize that the reason it was downgraded to gold was
because it had such flaws.

"Hoho, hahahaha!"

Wunue suddenly burst into hearty laughter.

After all, she wasn't asking for two pills for herself, but one for her
master and one for her friend.

How could Great Revival Pills be treated like mere candies?

"Then, what about martial arts? You must be well aware of the
functions of the Yijin Cleansing Method, yes?"

"Oh. That. Actually, I already learned it…"

"What?!"

Wunue jumped a foot in the air while seated, which was quite a feat,
before landing. Then, he furrowed his brow, looking stern, and sank
into thought before nodding.

"Since the Buddha's Palm reached you, it wouldn't be strange for the
Yijin Cleansing Method to have reached you as well. Then, have you
learned any other arts of the Shaolin Temple?"

"Just those two."

"Then, how about receiving another Divine Art in return for the
Buddha's Palm? Since you've learned the Yijin Cleansing Method, you
should be able to use it without issue. You must have experienced the
Hundred Steps Divine Fist, and there's also the White Lotus Divine
Fist, the Great Strength Vajra Palm, the Linked Nine Styles, and the
Unshadowed Swift Kick. Which martial art do you desire?"

"I am a swordsman, and I already have supreme footwork techniques.
You saw me using the Ethereal Steps, didn't you?"

"I thought you would say that."

Wunue nodded and spoke.

"Amitabha, there is nothing in the world that is not destined. Perhaps it
was inevitable that the teachings of the Buddha reached you. This
monk is still lacking, you see."

To be honest, Wunue was feeling ashamed.

How could a Buddhist monk say that a human could not overcome their
destiny?

The teachings of the Buddha sought to break free from the cycle of
suffering in the mortal realm and to escape reincarnation. In a way, it
was about cutting off the cycle of the grand scheme, defying one's
destiny.

Having pursued the perfection of selflessness for a lifetime by defying
destiny, how could he dare to predict that a promising youth would not
succeed?

Moreover, the child was one who embraced Heavenly Slaughter, yet
still possessed virtue.

According to the words of the Sutta Nipata, one of the oldest and most
primary scriptures of the Pali Canon, the Buddha taught to overcome
the suffering of the world by not desiring, by having a mind free of
possessions and a heart free of worldly attachments.

Of course, it was true that Qing had no particular desire for elixirs or
martial arts.

She didn't need elixirs and she felt she could learn martial arts when
necessary.

But she was an absolute jar of greed for everything else.

If Wunue had seen Qing eat, or even just seen the attendant set down
snacks on the tea table, he would have recognized her hideous gluttony.
And he would have seen the burning world in the image of the
mercilessly crumbling snacks under her teeth.

But how could Wunue have known such a thing?

He was just embarrassed, sorry, and ashamed, but also thankful and
impressed by the child's willingness to return what was rightfully
theirs.

"Hmm. Alright. Since you're returning it, how about you write down the
Sutra of the Buddha's Palm?"

"Ah. Are you having me write it down? Honestly, I thought I'd just
recite it to you."

"What more would an old man like me memorize? Since you'll be
writing it down, it will be kept in the Scripture Library in your
handwriting, so you must write it neatly and with great care. In
exchange, even if you include your name as the author, I will not mind."

"Yes…"

Qing replied with a slightly dejected tone.

\textit{You little rascal, no, you little girl.}

Wunue burst into laughter.

In fact, including one's name as the author was no ordinary feat. It
meant that all future disciples of the Shaolin Temple who learned and
mastered the Buddha's Palm would have to pay their respects to one of
the nine ancestors, the one who wrote it.

Ximen Surin would probably snort at such a condition, but she
wouldn't say much either.

And there was more to what Wunue had to say.

"It’s not the old who should memorize things — it’s the young. Here. I will recite a Sutra, so listen and memorize it."