\chapter{The Appearance of the Divine Dragon (2)}
	
Qing dashed forward, skimming the ground.

As a result, Weolbong momentarily lost sight of her as her figure
suddenly dropped low, only to soar up from close by.

As such, Weolbong planted his two feet on the ground using the
Thousand-Catty坠 technique and raised both his forearms, sticking
them together to form an iron wall.

And then, a soft tap.

The sword strike that touched his forearm, which was full of Inner Qi,
was as light as a feather. It was clear that there was no intention to
attack, so Weolbong slowly lowered his arm.

Then, he saw Qing standing still, holding her sword.

"Venerable, what is the matter?"

"Just now, were you not about to block a sword strike with your bare
arm?"

"That is correct."

Qing was at a loss for words at the confident answer.

How could that possibly make sense?

How could he just raise his two forearms to block a sword, even if it
was a spar?

Even if it was a practice sword with a dull blade, covering it with Sword
Qi wouldn't make it sharp.

If covering it with Sword Qi suddenly created a blade, then who in the
world would bother carrying a sword?

They would just carry around a thin iron rod and emit a superheated
blade that seemed like something from a distant future space age.

Qing turned her gaze to the referee and host.

She was basically asking whether this was acceptable.

The referee's expression also turned strange.

"Ahem, Weolbong. Even if it was a blade wrapped in Sword Qi, could
you have blocked it with your bare hands?"

"This monk has studied the Diamond Unbreakable Divine Art, so my
body has already reached a point where it cannot be harmed by Sword
Qi."

"Diamond Unbreakable Divine Art!"

"If the Venerable wishes, you may use a real sword."

The referee looked at Qing.

"Young Lady, what will you do? Since the monk is so confident, will you
use a real sword?"

Since they were already in the middle of a spar, it would be awkward to
fetch a real sword now. Moreover, even if she used a real sword, could
she attack him at ease? If she cut him, it would only lead to bloodshed
at the sparring competition.

Furthermore, if she won a match of a bare body against a real sword,
there would definitely be chatter later.

She thought that perhaps they were being petty and sly, acting in a way
that favored them, despite being the so-called leaders and pillars of
the Orthodox Faction.

As the two contestants stood still and conversed, the murmurs of the
spectators grew louder.

Qing shook her head at that.

"It is fine. Then, I shall go again."

Thus, the spar resumed.

Qing first wrapped her sword lightly with Sword Qi to test the waters.

The gently extending sword strike was more about lightly swinging
without much force, rather than displaying the profound mysteries of
the sword.

In response, Weolbong raised his forearm at a right angle and easily
blocked it.

Thud. The impact transmitted to her hand was extremely solid. It felt
like hitting a boulder.

Qing gradually increased the intensity of her attacks.

Weolbong blocked them one by one accordingly. It was an art where
even trajectories that seemed intentionally missed were blocked with
his arms, as if to say, 'Cut me if you can'.

Only when Qing's Sword Qi gradually thickened and drew out strands
of entangled threads did she feel a certain conviction.

Hm. He really can block even a real sword, huh.

But it was still vague.

Could he block a cut to the neck? What about other vital points? What
about the stomach? What about a stab to the solar plexus? No, that
doesn't make any sense.

However, Weolbong seemed to think he had sufficiently demonstrated
his defense. He then began to unfold the initial moves of the Shaolin
Fist's supreme technique, with the momentum of a charging beast
covered in a heavy shell.

Thankfully, they were familiar movements.

The straight punch was the Big Dipper Serialization of the Seven Stars
Fist. As she lightly twisted her body, his arm, bent at a right angle,
rotated and the back of his hand aimed for Qing's face.

Qing leaned her upper body back, and the fist stopped right in front of
her chin, shaking the veil. It was the maximum rotation for a human
elbow.

After deflecting the light combination, it was Qing's turn again. Qing
stepped on Weolbong's foot, which was completely sideways, and
pushed his other foot.

What the hell? Why isn't it budging?

However, since the leg that was firmly planted on the raised platform
didn't yield, it was rather Qing's balance that wavered, causing her
body to lean.

She supported herself with one arm on the ground, spun around twice
like a swallow, and then saw Weolbong, who had quickly closed in,
mounting a horse stance and loading both fists at his waist.

Front? Back? There was no time to 고민. Weolbong's thighs seemed
to double in size. Thump! Qing stomped on the ground and launched
herself into the air.

At the same time, Weolbong's double fists extended. Two arms
stretched out from the body, planted on the ground. The twin fists,
loaded with immense power, narrowly brushed the soles of Qing's feet
as she soared.

Thud! Qing's knee struck Weolbong's forehead.

My knee! As her knee joint creaked in pain, Qing swallowed a scream
and used one arm to do a handstand on Weolbong's rough head.

How can it be so hard?

Since she didn't want to just pass by, she struck the bluish bald head
with the end of her sword's hilt and used that recoil to leap away,
landing on the ground.

Weolbong staggered slightly, but that was it.

Qing licked her lips in disappointment. She should have hit him harder.
She had held back, fearing she might crack the monk's skull, but he
seemed to have taken no damage.

However, his ears were slightly red, probably because blood was
rushing to his head. Hm. Is he pissed?

"Haap!"

Weolbong charged forward again.

Qing retreated with large strides and unfolded a series of sword strikes.

Thud! Thud! Thud! Thud! Although her strikes lacked power due to her
retreating steps, it was quite disconcerting to see him furiously
advancing, hitting them away with his fists and arms.

Originally, the purpose of a weapon was to touch the opponent's body.

Since human flesh could not withstand weapons, a dramatic union
would occur the moment they touched, whether it was a stab, a cut, or a
slash.

However, the Shaolin monks seemed to completely deny this basic
principle.

Then, Qing, too, couldn't help but admire.

No wonder the monks of Shaolin, who don't even use weapons, are
considered the greatest martial artists under Heaven. I mean, how can
you block a sword with your bare hands?

Hm. Do monks know the White Hand Demonic Arts too?

It seemed like a reasonable suspicion.

But when it came to hardness, the Diamond Unbreakable Divine Art
was specifically for that purpose, while the White Hand Demonic Arts
was more of a bonus that came with it. As such, there was no need to
compare which one was stronger.

The seventy-two arts of Shaolin burst forth, an unlimited combination
of arms, fists, backhands, palm strikes, hand blades, and even kicks.

Since he was hitting away the sword with his bare hands, offense and
defense were one, leaving Qing with no other choice but to retreat and
scatter her sword.

In an instant, over ten exchanges passed, and Qing's retreat exceeded
thirty steps.

However, a person walking backward could never be faster than one
walking forward.

Moreover, the footwork of Shaolin was all about advancing forward with
fierce charges, so the distance gradually narrowed until one of
Weolbong's feet was just a step in front, with his legs wide apart.

Ah. Something big is coming. Qing had a hunch.

Indeed, the extended palm aimed for Qing's eyes while the tightly
coiled fist shot out with a menacing boom, piercing Qing's abdomen
and emerging from her back.

Of course, it didn't actually happen, but that was what it felt like. It was
just that there was no bloodshed at the sparring competition, for Qing
had evaded it by leaving behind an afterimage, using the footwork-
Formation combination technique of the Evasive Steps.

Having suddenly lost his target, Weolbong did not panic, for he had
seen Qing's Evasive Steps from afar. He immediately aimed his fist at
Qing.

Then, he took a big step forward while turning, extending his fist in a
straight line-

Feeling a chill, Qing urgently drew upon her Inner Qi.

As she pushed her output to the limit, her Sword Qi surged, instantly
making the blade seem five times larger. The greatsword fell with the
momentum of splitting something in two. Boom!! With a loud noise,
Qing's Sword Qi shattered like a fan, scattering wildly behind her.
Qing was pushed back.

Even though her hands, trained by the White Hand Demonic Arts, felt
like they were being torn apart.

It was Shaolin's famous Divine Art, the Hundred Steps Divine Fist.

Wow, if I had been hit properly, I would have been laid out on the
ground.

If she gave him any distance, his ridiculously powerful attacks would
come flying.

As Weolbong stretched out both arms and straightened his bent leg,
the heel of his rear foot slightly lifted.

Qing subtly shifted her feet, calculating the angle.

Finally, at the moment Weolbong's body turned, Qing stomped on the
ground of the sparring platform, almost shattering it, and charged
forward.

Whoosh! The aftermath of the Hundred Steps Divine Fist brushed past
her ear. Despite having dodged it generously with a considerable
distance, the aftereffect still tickled her ear.

Qing's footwork drew sharp, lightning-like trajectories, alternating left
and right as she advanced.

It was a completely different footwork from the elegant and leisurely
Yue Maiden's Steps, a peerless Qinggong that made Shinto what it was,
the Empty Flash.

However, since it was not a Qinggong to show off to others, no one
recognized it.

Qing's Sword Qi left afterimages, striking Weolbong like a bolt of
lightning.

But the moment it touched, Weolbong's body suddenly disappeared, a
technique Qing also used, the Iron Plank Bridge. It originated from
Shaolin's arts, so he could be called the original.

Weolbong, springing up like a spring, extended his palm downward. A
palm strike was when one struck with the lowest part of the palm,
where it met the wrist. It was as hard as bone, with no loss of power,
making it a formidable technique.

Weolbong's palm strike drove into Qing's abdomen.

Thud! Despite bracing her abdominal muscles, she felt a rush of breath
leaving her body, making her wheeze.

It wasn't a proper strike that continued from the footwork, but an
awkwardly executed attack using only the wrist's flexibility, so its
power was insignificant. That was why she could endure it.

Qing slammed her sword into the sparring platform and struck
Weolbong's chin with her fist. Since a swordsman had let go of their
sword, Weolbong was caught off guard and his chin was hit.

In fact, Qing had also mastered about thirty of the seventy-two arts of
Shaolin. The unarmed martial arts commonly sold in the marketplace
were mostly degraded versions of those. And since she had raised all
those white-bordered, common martial arts to the tenth level as soon as
she acquired them, they took up almost no Practice Points anyway,
being such trivial skills.

Weolbong staggered, and Qing, with a vengeful heart for her aching
abdomen, struck his solar plexus very hard. However, Weolbong's palm
blocked Qing's fist in front of his solar plexus.

But Qing had monstrous strength, so Weolbong, having struck his own
solar plexus with the back of his hand, gasped for breath.

Qing's eyes sparkled.

As she retrieved her fist, she leaned forward, and with the force of
stomping on the ground, her elbow extended.

It was a perfect execution of the Outer Gate Elbow Strike.

Thwack!! After adding another hit to the solar plexus, Weolbong
exhaled the last of his breath. Qing then tried to turn her body in the
opposite direction and strike with her shoulder using the Iron Mountain
Lean technique-

"Argh!"

It was too common a technique, and trying to use it against a master
who had properly learned it since childhood was too careless.

As a price for her carelessness, Qing took a hard hit to the side and
snatched the sword she had stuck in the sparring platform, quickly
creating distance.

"Ugh. That hurts……"

Qing rubbed her stomach and massaged her side, frowning.

Weolbong, on the other hand, was catching his breath, wheezing
heavily as he tried to recover from having been struck twice in the solar
plexus.

Qing was thinking about how to beat him to make him admit defeat
and step down.

Suddenly, Weolbong raised his palm.

"This monk surrenders. I apologize, but this monk dared to
underestimate the Venerable. The reason why Teacher told me to do my
best."

"It sounded like you were saying you weren't giving it your all until
now. Is that right?"

"Yes. If you happen to be injured, please do not hesitate to surrender."

Then, a golden Inner Qi flickered in his fist, shining brilliantly.

-Ooh! Fist Force!

-A Transcendent! A Transcendent Realm martial artist!

At the same time, the spectators who had been holding their breath
and watching the spar burst into cheers.

Regardless, it was not good news for Qing