\chapter{The Appearance of the Divine Dragon (18)}

Although the competition ended with an unexpected incident, there was
no need for a strict judgment to determine the winner or loser.

While Qing was in a trance, Gongson Yoyae took all her attacks like a
punching bag, receiving them head-on with all her might.

It was a desperate effort to accommodate Qing's enlightenment.

That last move. Thousands upon thousands of flower petals filled the
entire area, each one actually a blade capable of piercing through
human flesh and bones without any resistance.

If Qing had been filled with killing intent, Gongson Yoyae would have
been turned into finely minced meat.

The reason the platform collapsed was simple. Due to the continuous,
intense sparring that was more violent than usual, the wood itself was
bruised and cracked, accumulating fatigue.

On top of that, Gongson Yoyae's Yeoui Staff-like Sword Qi had
inflicted damage to the structure, and then the petals made of Sword
Force had extensively scratched it.

Eventually, the structure could not bear its own weight, with the
breaking point causing a chain reaction, resulting in a total collapse.

The plans of the Wulin Alliance for the event went down the drain, as
did the cost recovery for building the platform.

And then, Qing went kerplunk.

It was unclear why the Eighth Move of the Solitary Nine Swords,
Boundless Variety, had suddenly been unleashed when she was in a
trance.

Perhaps the image of the Celestial Martial Emperor she saw on the
Absolute Sword Wall was too striking, or maybe she subconsciously
wanted to show off after crossing the wall, or it could be that her
unconscious mind released it all at once in an attempt to protect her
meridians when her True Qi surged all at once. It was not for certain.

However, the Celestial Martial Emperor was an immortal Master who
was born human but did not die human.

To think she had dared to imitate such a Master's enlightenment that
he had left behind in his later years.

If a sparrow chased after a stork, it would split its legs; so it was only
natural for Ximen Qing to experience extreme exhaustion, leading to a
total shutdown of all her muscles.

It was a wondrous move that anyone, regardless of their knowledge of
martial arts, would not see again in their lifetime. But for those who
knew martial arts, it was even more astonishing, proving that the more
you know, the more you see.

There was just one strange thing, though.

Among the five-colored Sword Force, the yellow had the golden light of
Buddhism mixed with the Qi of Daoism, and the blue was the pure and
clear True Qi of Daoism.

The red, which was as lustful as it could be, could be considered a
traditional Immortal Arts of Daoism, focusing on harmony and
longevity.

But the white and black… especially the black. It was an aggregation of
the most wicked Demonic Qi in the world, carrying such a hideous
depth of malice.

It was impossible for a single person to possess such a diverse range of
True Qi to the extent of forming Sword Force. So, perhaps the Celestial
Martial Emperor had devised it through some unique method.

Since it's called Boundless Variety, the nature of the True Qi could
also change. He is indeed the Celestial Martial Emperor! He is indeed
our Senior!

That was the general consensus.

Only Ximen Surin, who was listening quietly, struggled to hide her
bewilderment.

Thus, Yuha Jinin asked.

"Youngest Sister. Was that not the Boundless Variety, the move of
Senior Celestial Martial Emperor?"

"Uh, um. It probably is."

In any case, since Qing had no memory of using the Solitary Nine
Swords, she could only give a vague answer.

"It was truly a god-like move. To hide a blade within beauty, that is the
spirit of Mount Hua. That must have been what the Celestial Martial
Emperor intended. Mm. But you said you don't remember?"

"Yes. It seems I am still far from reaching the level of Senior Celestial
Martial Emperor's martial arts."

"Well, you have just stepped into the Transcendent Realm, so it cannot
be helped. Do not worry too much and proceed slowly without haste."

At that, Qing looked at the bundle of paper and the writing brush that
Yuha Jinin held tightly in his hands.

As soon as she had arrived, he had asked if she could annotate the
moves, so it seemed like the one who was worried and impatient was
actually Grandfather Yuha Jinin.

At that gaze, Yuha Jinin coughed and handed over what he was holding.

"Ahem, it's not that. I heard you were fond of writing, so I brought this as
a gift. Isn't it a great gift to be able to see the teachings of the Absolute
Sword Wall with your own eyes before you die?"

For such a claim, the paper was white and bright with a tranquil pattern,
the highest quality among the highest quality, but the writing brush
was not particularly high-end, giving the impression that he had just
picked it up because it was within reach.

"But it is said that the Boundless Variety is the Eighth Move, right?"

"Yes. It is called the Eighth Move, Boundless Variety."

"Khehehe, did you hear that? It is the Eighth Move, they say. Since there
is a separate move for each of the Nine Great Sects, what does it mean
for it to be the Eight Move?"

"Kehum."

"Hm, hm."

"Keheum."

The elders of the Nine Great Sects, who had come to offer their
congratulations, coughed uncomfortably.

Originally, the later the position of a move, the more profound,
difficult, and powerful it would be. If the Mount Hua Sect's move was
the Eighth Move, it meant they were placing themselves above one
while stepping on seven below.

"Each move describes a different enlightenment, so what does it matter
which comes first and which comes later? What a tasteless thing to say
for a Daoist. This is why those from Mount Hua are always mocked."

The one who retorted was the Sect Leader of the Wudang Sect,
Chaegeon Jinin.

"What did you say? Ha, I see that the move left in Wudang is exactly the
First Move. Besides, wasn't Tai Chi originally an enlightenment
obtained from the Zhen Family?"

"What does it matter if it is the First Move or the Ninth Move? It is
childish to rank them based on such things. If you have already reached
such an age, you should know how to be prudent and not act like a
child, ranking them. Tsk tsk."

For reference, although no one at this place knew, the ninth move of the
Solitary Nine Swords was in the Wudang Sect.

Perhaps Chaegeon Jinin would later ponder deeply on the meaning of
the phrase 'your mouth is your own worst enemy'.

Then, Great Monk Wunue chided them.

"Stop it, both of you. Aren't you ashamed to act like this in front of your
Youngest Sister?"

"Keheum."

"No, what do you mean Youngest Sister, ahem. She is indeed
young."

Indeed. Qing was technically a direct disciple of Ximen Surin, and
another direct disciple of Ximen Surin was Wang Juhee of the Heavenly
Sword Alliance, who was also the Sect Leader of the Divine Maiden
Sect.

"Hm. Speaking of which, didn't the child say she wanted to see the
Absolute Sword Wall? Since we are talking about it, let's all go and see it
together. It has been a while since I wanted to see our Senior's
traces."

"Kehum. Youngest Sister, if you are returning to the Divine Maiden
Sect, you can make a slight detour to Mount Zhongnan, can't you? You
can stop by Mount Song on the way."

"Then, while you are at it, you could also visit Mount Kongtong."

"Yes. After visiting Mount Kongtong, come down to Sichuan and see the
Absolute Sword Walls of Qingcheng and Emei before returning by
boat."

"If you're going that way, you should also stop by Diancang……"

"Diancang? Are you trying to send a person all the way to Yunnan?"

They were all clamoring to have her visit their Absolute Sword Walls.

Honestly, the real reason they had gathered was not to celebrate the
new Divine Dragon and offer words of blessing, but to invite her to see
their Absolute Sword Walls.

Even for the past champions, the Divine Dragons, there had never been
an instance where all the elders of the Nine Great Sects gathered in
one place to offer their blessings.

It was customary to visit each one individually to pay respects and
receive their blessings. As such, if others were to hear of it, they would
tsk and say that the old folks had lost their minds.

Just like Chaegeon Jinin.

"What do you expect her to learn from just looking at it? You're just
pressuring the child, making her feel obligated to visit when she said
she was going home. Tsk tsk. She just gained enlightenment, so shouldn't
she take some time to organize her thoughts?"

At that, the other Sect Leaders, or the elders who had come as proxies,
glared at Chaegeon Jinin.

For reference, the Wudang Sect was the closest neighbor to the Divine
Maiden Sect. If one were to ride a carriage from the Divine Maiden
Sect, it would be impossible to take more than three days, no matter
how leisurely one traveled.

"Mm. Girl, about Kunlun. Um. Right. Um."

Cheonbija Jinin of Kunlun trailed off.

Honestly, he felt that his conscience was too outstanding to ask her to
stop by Kunlun.

But it was the insight of the Senior Celestial Martial Emperor.

Moreover, it was a great legacy that he had left as a reward after
personally witnessing the supreme techniques of the Nine Great Sects,
reinterpreting them.

Even the current Greatest Under Heaven, Wunue, felt a sense of
something stirring within him whenever he looked at the Absolute
Sword Wall. As such, it was an extremely valuable gift of the heavens
to realize the interpretation of such a peerless Divine Art.

"Since Master has already told me to follow the teachings of Senior
Celestial Martial Emperor once I reached the Transcendent Realm, I
was planning to visit each place anyway. I am truly grateful to be
welcomed even before I had the chance to do so."

Qing said with a bright smile.

At that, the elders of the Nine Great Sects realized with a throbbing
heart.

This is why people want to have daughters!

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Behind the introduction stage of the new Divine Dragon. The term
'Divine Dragon' itself meant a new dragon, so saying 'new Divine
Dragon' was a bit awkward, but since Divine Dragon was practically a
proper noun referring to the winner of the competition, it was not a
huge issue.

Ye grabbed Qing's hand tightly.

"Young Lady Ximen. Congratulations."

"Mm. How are you feeling, Ye? I heard you took quite a beating while I
was in a trance. Are you okay? How is your body?"

In fact, while holding Qing's hand, the left hand of Gongson Yoyae,
which was attached, showed thick, dark bruises.

"Please do not be sorry. In truth, I also grasped a clue to the
Transcendent Realm while facing Young Lady Ximen's sword. I should
be the one thanking you, instead."

And Gongson Yoyae smiled brightly.

"And above all, it was such an enjoyable time. If I could do that again, I
feel like I could do anything. Perhaps, it might not be so enjoyable
again for the rest of my life."

"Uh, um. Don't talk like someone who isn't going to live very long. How
is your body? What about your Innate True Qi? Did you use too much of
it? Can you tell how much your lifespan has been reduced? I can't have
that. I'll give you a Great Rejuvenation Pill, so-."

"I appreciate your concern. But I have already rested well and taken
elixirs. My family would not have made no preparations for an event
that our very fate depended on, right? I have taken various types of
elixirs that replenish the body and True Essence, so please do not worry
any further."

"Hmm. Various types? What did you take? Can you tell me? If you're
just saying that because you feel burdened about taking a Great
Reversionary Pill, I will seriously not let this go."

"First, there was the Grand Purity Pill, two Lesser Reversionary Pills,
the Celestial Elixir of Kunlun, the Sun-Heaven Two Elixir, the
Radiance-Spirit Revival Pill, the Self-Nourishing Protection-Speeding
Pill, and the Amassing Qi-Nurturing Pill. I have taken a solid amount of
them, you see? They are all rare elixirs that you have likely heard of at
least once. The undigested energy of the elixirs is abundant in my
body, so if I were to take a Great Reversionary Pill now, my meridians
might burst."

"Ah."

Qing was startled and secretly put the Great Reversionary Pill she had
hidden in her sleeve back into the box.

If she had just shoved it into her mouth during a moment of
carelessness, it would have led to a major incident.

And Qing reflected a bit.

Gongson Yoyae wasn't some tragic protagonist locked in a training
room, being abused by her family.

Her family was likely doing their best for her.

It was evident just from hearing the names of the terrifying elixirs.

But then again, I've never heard of those……

I know there's a Lesser Reversionary Pill because there's a Great
Reversionary Pill. Um. The rest… I don't know. They must be good or
something.

Finally, as their names were called, they came out to the stage. And
Qing realized what it meant to hear a sound that was so loud it was felt
through the body rather than heard through the ears.

This time, there was no one to stop the cheering, so the fierce
acclamations continued endlessly until everyone's throats were hoarse.

Of course, there were some offensive shouts like Three Heads, Four
Limbs, and Absolute Beauty, but there were also some nice words
mixed in, so she was satisfied.

She had never heard of the Moonlight Sword, and though the Celestial
Martial Maiden sounded like some kind of shaman, it was still okay.

The Most Beautiful Under Heaven was going too far. And what use
would there be for me to be pretty? I need other people to be pretty.

The Sword Phoenix sounded a bit off.

And what in the hell is the Vermillion Bird Maiden?

There were numerous attempts to give Qing a title, but unfortunately,
the fairest means, majority rule, could not be achieved.

This was because Great Monk Wunue suppressed them all with the
weight of being the Greatest Under Heaven.

Although Yuha Jinin complained, saying he had decided on it first,
even he had to acknowledge that a three-letter title was much more
precious than a four-letter title, and since it was more precious, it
carried more authority.

Above all, he liked the fact that the new title shared the character 'Hua'
with the Mount Hua Sect, emphasizing their connection.

Thus, the current Greatest Under Heaven bestowed a title to the
talent most likely to become the next Greatest Under Heaven.

The Heavenly Beauty Sword.

The most beautiful sword under the heavens. 