\chapter{The Appearance of the Divine Dragon (16)}

Usually, as a martial artist's realm rises, their insight sharpens
along with it. This is because Masters see the world from a broader
perspective.

Just as Ximen Surin could sense Qing's Heavenly Slaughter by feeling
her pulse, a great martial arts master could perceive it just by meeting
her gaze.

On the other hand, Tang Nana would always take her pulse and say
things like, 'Yep, yep. You're healthy again today, huh?'

Thus, the insight of a martial arts master who was the Greatest Under
Heaven contained an unimaginable amount of information.

And that martial arts master saw Qing's Demonic Arts, a strand of the
cursed lightning from the condemned Violet Lightning Demonic Arts,
one of the Ten Great Demonic Arts Under Heaven.

And so, he exclaimed with wide eyes.

"Oh my. Such pure Daoist True Qi. A momentary path from the heavens
to earth. It is truly worthy of being called an Immortal Art. But what
martial art is this? Was there such a martial art in the Divine Maiden
Sect?"

Of course, gaining more information than others did not necessarily
lead to the correct answer.

At that, Wudang's Sect Leader, Chae Geon-jinin, replied.

"Doesn't it feel similar to the Grand Violet Mist Divine Art?"

At that, the owner of the Grand Violet Mist Divine Art, Huashan Sect's
Sect Leader, Yu Ha-jinin, snorted and interjected.

"Hmph. What are you talking about? Why don't you just say it's the
Violet Lightning Demonic Arts?"

Then, Chae Geon-jinin responded.

"Since you were bragging about the Crescent Moon Divine Sword and
the Future Number One Under Heaven, I thought you had a hidden
daughter and passed down the Grand Violet Mist Divine Art."

"Bragging? Just look if you have eyes. Is that a level of martial prowess
that a mere twenty-year-old could display? You should improve your
insight."

"What did you say?"

"Hmph."

Huashan and Wudang, arguing over which was the best sword sect
under heaven, were long-standing rivals, so it was a long-standing
tradition for their sect leaders to bicker.

In any case, it was irritating to see Yu Ha-jinin boasting as if he had a
secret daughter.

After all, it was not boasting about the Divine Maiden Sect's disciple,
but rather about his own insight.

So, Chae Geon-jinin watched Qing's duel with a critical eye.

Even in the midst of it, his martial insight let out a 'Hm?' sound,
expressing a sense of peculiarity.

Something… This sword stance… It seemed familiar.

It was certainly… off. That momentum was like… Evil.

It was then.

Chae Geon-jinin, who had been watching Qing's duel, hoping to find
some fault, clicked his tongue.

"A child of the Dao is using such vicious killing swords. Her Qi is pure,
so it is of the Dao, but the user wields it like an Asura or Rakshasa. At
this rate, how can she reach the peak?"

A Rakshasa was a divine being who converted to Buddhism, but when
referred to as an Asura Rakshasa, it meant an evil spirit that devoured
humans before its conversion.

Then, Yu Ha-jinin retorted.

"If you're going to swing a sword, shouldn't it be a killing sword rather
than a saving sword? Even after seeing such pure Dao Qi, you call her
an Asura Rakshasa? Why not just call it the One-Hundred-Eight Asura
Sword? Why, that's the Black Slaughter Demonic Palm, no, since the
child's hands are so fair, why not say she's using the White Hand
Demonic Arts? Why not just curse her as an evil cannibal who has
mastered all Ten Great Demonic Arts Under Heaven?"

If Qing had heard this, she would have suggested he retire from being a
Daoist and set up a shrine to become a shaman, given his astonishing
accuracy.

It could be said that he possessed insight worthy of his pride and
boasting.

Then, Chae Geon-jinin became embarrassed.

He just dislike Yu Ha-jinin; he had no ill will towards the Divine
Maiden Sect's disciple.

"Hmph. Who said it was Demonic Arts? I'm just saying her Killing Qi is
too strong. Is a sword with Killing Qi a weapon a Daoist should wield?"

"If it's made to be a sword, then it should be used to stab. What, is he a
quack who's going to save people with a knife instead of being a
doctor?"

Huashan's swords were beautiful, but also vicious killing swords. On
the other hand, Wudang's swords only turned back the sword strikes
and did not directly harm, so they boasted that their swords were for
saving lives.

"Ahem. With elders present, how could you act so childish? You two
should restrain yourselves. And Yu Ha-jinin is right. If you're going to
hold a sword, shouldn't you stab with it?"

Kongtong Sect's Sect Leader pretended to mediate but threw in a vote
for the killing sword. This was because Kongtong Sect's martial arts
involved taking flesh and bone to reach for the heart, utilizing an
extreme form of the killing sword.

At that, the elder of Zhongnan nodded.

"These guys who have only trained in killing techniques are banding
together. Aigo, Senior Martial Arts Uncle. The path to saving people is
so difficult."

Chae Geon-jinin asked Wunue for help.

Shaolin's martial arts were for saving lives. Of course, it was
questionable whether crushing all the bones of an evil-doer and
crippling their tendons before locking them up in the Repentance
Chamber to live on, just barely clinging to life, could be called 'saving
lives'.

"Ahem. Still, saying she's mastered the Ten Great Demonic Arts was a
bit much, wasn't it, Chae Geon-jinin?"

Martial Arts Master Wunue had already given his heart to Qing, the
'Elderly Slaughterer', so he only lightly rebuked, telling him not to
mention the Ten Great Demonic Arts, even as a joke.

Then, 'Amitabha, but what was I thinking about again? Why did I think
that child, Ximen Qing's, martial arts were familiar?' he thought.

"Senior! What are you saying. Uh? But wasn't the one who mentioned
the Ten Great Demonic Arts that guy? Why are you scolding me?"

"Hahaha, you brat. This is the principle of Yin and Yang Tai Chi. You
still have a long way to go. You should try to see only the good in
people. Why do you only focus on the shortcomings?"

Yu Ha-jinin teased.

"Urgh."

Chae Geon-jinin clenched his fist in frustration.

To think he would be defeated by a Huashan boor in the principles of
Tai Chi. He felt an unparalleled sense of shame and humiliation.

Meanwhile, Qing's palm was aimed at Gongson Yeyeh's solar plexus.

Realizing it belatedly, Gongson Yeyeh instead leaned her body forward,
offering her chest instead of her solar plexus.

It was a rational decision to offer her chest instead of her solar plexus.

Gongson Yeyeh made a sound, her breath catching in her throat from
the pain. 

'Ah, that really hurts'. Qing slowed her attack, hesitating.

If it were a life-or-death duel, the outcome would have been decided
then and there.

This was because the White Hand Demonic Arts was originally a
vicious Demonic Art that used penetrating strikes to tear apart Qi and
blood.

Penetrating strikes that inflict permanent damage to Qi, blood, and the
dantian were the White Hand Poison of the White Hand Demonic Arts.

However, she couldn't bring herself to do that to Gongson Yeyeh, so she
had already struck several times with just the form of the attack.

If it were a life-or-death duel, by this point, her opponent's internal
energy would be tangled and their Qi and blood would not circulate
properly, causing them to stagger. But she couldn't just ask the
referee, 'Hey, I hit her with the White Hand Demonic Arts several
times already, so can you just make a ruling on this?'.

Then, is this serious?

"Whew. Whew."

Gongson Yeyeh looked like she had taken a dip in a bath. The contents
of the duel were intense, but using Innate True Qi itself seemed to
consume a lot of stamina.

But her expression was bright.

Qing couldn't understand.

Why, why does she look so happy?

I think I hit her pretty hard, you know? Doesn't it hurt?

However, Gongson Yeyeh was simply tenacious. It was almost a gesture
of affection, a temptation to say, 'I am here, so will you not swing your
sword even so?'.

Qing now understood.

A lonely person who had been training alone in the training hall all her
life. However, Gongson Yeyeh's past was not a painful memory.

The expression of someone who affirms that the hardships they could
not have endured were what made them who they are now.

That is why we are sharing swords like this, are we not?

I am doing my best like this. Just as I have done every moment.

The expression of Gongson Yeyeh, burning her own life force yet
finding joy in this moment, was truly dazzling.

What is so important about using a bit of tomorrow for today's
enjoyment?

For Gongson Yeyeh, martial arts were the only thing she had in life,
and therefore, something enjoyable.

But what about me?

For Qing, martial arts came with painful memories.

Falling into an unfamiliar world with an unfamiliar body, in the midst
of contempt, persecution, and ridicule, it was the only way to survive,
a way to live, because she had to live.

For Qing, martial arts were a means to take.

The back alleys of Zhongyuan were a harsh gutter where
compassion could not take root, where everyone was too hungry to be
generous and give to others.

She still vividly remembered that time, the feeling of choking the life
out of someone, the despair, the realization that she had crossed a line
of no return, and the premonition that this sensation would be
branded into her for the rest of her life.

But it wasn't like that, you know?

Now that I think about it, what was the big deal about killing a piece of
shit who deserved to die? I should have been proud of myself for
cleaning up some trash that killed a kid just to get a few extra coins.

It was a shameful memory of running away, crying like a fool while
clutching just one trophy.

Ah. That's right. Moonlight Sword, Number One.

It was the first item Qing had ever taken from someone else by killing
them. To be precise, it was an item she had killed someone to take.

There were all kinds of trash in the back alleys, so it was a den of
bastards who would die anyway, but the reason she killed that
particular guy was because she wanted a sword. After all, she had
swordsmanship but no sword, so what could she do?

A sword that was half-broken and rusted.

A scrap piece of metal that no one would even bother to take even if it
was given away for free.

Qing killed a person to obtain that piece of trash.

My Moonlight Sword, Number One. No, back then, it wasn't even
Number One yet.

My Moonlight Sword. My treasure.

I used it until it completely broke and fell apart piece by piece in my
hand. I even made a grave for my treasure, which was shattered to the
point where only the handle remained, burying it in the foothills of
Jianping.

And even after that, I promised in front of its grave that every
subsequent sword would be a Moonlight Sword.

Suddenly, she remembered her master's words.

A sword held in the heart.

Ah. That's right. I had forgotten about the glorious origin of the
Moonlight Sword for far too long.

A smile formed on Qing's lips.

The sword she had obtained was so precious that she would hug it
tightly when she slept, and she would carefully thrust it, worried that
the blade might get damaged. In fact, she never even tried to slice with
it.

Back then, it felt like I could do anything with just one sword.

Suddenly, the memory of her hand came back to life.

The balance was off, the grip was slippery with hand sweat, and it was
fortunate that the broken cross-section was quite sharp.

Back then, she didn't have Demonic Arts or anything like that.

It was just the Yue Maiden Swordplay. The only swordsmanship she
possessed.

My sword. My swordsmanship.

In this uncivilized and primitive medieval land of China, it was what
allowed me to think about tomorrow.

It was what ultimately helped me hope that things would get better.
Qing naturally performed the Yue Maiden Sword.

First Movement. A Drifting Child Picks Up a Stick.

Qing's sword drew a bizarre trajectory. To be precise, it was more
awkward than bizarre.

It was like a child picking up a long stick and swinging it around in
glee, with no particular purpose or effectiveness, just swinging for the
sheer joy of it. It was the discovery of the primal joy that humans
possess.

Just a well-extended stick.

To a child, it would be no less than the greatest sword under heaven.

Just as my Moonlight Sword, Number One, was to me.

Gongson Yeyeh twisted her body in a hurry at the sudden thrust of the
sword. Because there was no particular technique in the way it
extended, it was rather unfamiliar and difficult to deal with.

Swinging, stabbing, and sweeping left and right without meaning, yet
suddenly threateningly entering under the chin.

Gongson Yeyeh looked at Qing in surprise.

Did she still have hidden swordsmanship? Just how great of a person
was Young Lady Ximen? It was an expression filled with affection and
anticipation.

However, Gongson Yeyeh was once again surprised.

It was because she couldn't meet Qing's eyes.

With her eyes closed and a soft curve to her lips, she lightly danced,
scattering her sword. 

Gongson Yeyeh held her breath to the maximum
and carefully suppressed even the sound of her harsh breathing.

After all, she couldn't disturb a swordsman who had fallen into a state
of selfless trance. 