\chapter{The Appearance of the Divine Dragon (10)}

With his mouth agape, he froze, his eyes darting left and right, like a lazy frog waiting for a fly to come by.

Then, Wunue suddenly raised his voice.

"You, child, child, you!"

"Yes? Did something go wrong? Ah, perhaps it didn't dry properly and got smudged-"

"That's not it. Sanskrit, you know Sanskrit?"

Sanskrit was difficult.

It was originally the script used by monks, and the monks of Cheonchuk were all aristocrats of the highest order who treated the common people like livestock.

And here, livestock did not mean an insult, but rather actual, literal dirty animals. If a commoner's skin so much as brushed against a monk, they were executed for the crime of a filthy beast defiling a priest.

Therefore, the language of these monks had to be special. It was intentionally made difficult so that the dirty animals could not dare to read or write it, and that was Sanskrit.

For starters, there were no spaces between words. Not only that, but all the letters in a sentence had to be connected, so the basic form of each letter changed depending on the beginning, middle, and end of a word.

This resulted in a terribly complex set of variations, with different verbs for each subject, changes depending on tense, and nouns, verbs, and adjectives all having separate masculine, neutral, and feminine forms, as well as singular, dual, and plural forms.

On top of that, it was even a phonetic script, so it had to be written exactly as it sounded.

If the insult 'You acted like shit, you piece of shit' were to be written in Sanskrit, it would be 'Youactedlikeshatyoupieceofshat'.

Therefore, it was said that it took ten years to speak it properly, ten years to just read it, and another ten years to write it.

As a result, even learned monks of Shaolin began to study Sanskrit scriptures only after their hair had turned white.

To think that a twenty-year-old girl could use it so neatly was nothing short of astonishing.

Could she be a princess from Thianzu?

Come to think of it, those large eyes that seemed to pop out at any moment looked a bit sunken, which was somewhat reminiscent of that region? Or was it not?

But her skin was as white as snow, so she couldn't possibly be from there.

"Ah, should I not have used Sanskrit? But I provided annotations for each sentence……"

The original text written in Sanskrit was annotated in Chinese characters.

Sanskrit had a distinct shape and clear distinctions, so there was no confusion, and each Chinese character was filled with power, as if it were alive.

The small letters were as uniform and neat as if they had been typeset, which was also a remarkable feat.

But the contents could be reviewed slowly. Wunue frowned.

"You did not write your name as the compiler?"

"Is there a need to put my name on it? You said it would be passed down for generations, so wouldn't it be strange to have an outsider's name stuck on it?"

As she smiled softly, Wunue felt a moment of shame.

To think she had no interest in the honor of having her name recorded in the Sutra Repository and being remembered forever as a benefactor of Shaolin.

Wunue had been seriously considering asking her to write a plaque. What was the point of letters when he was just being greedy?

Of course, Qing was just ignorant, so she didn't know.

In the first place, she hadn't obtained it through proper means, so she felt awkward.

"Now. Write it here. Seomun Cheong, a disciple of the Divine Maiden Sect, restored the lost technique through a fateful encounter and passed it on to Shaolin."

Wunue urged her, even offering a fine brush and a portable ink bottle.

Unable to refuse, Qing wrote the inscription, and Wunue watched the unfolding of the grand calligraphy in real-time, completely mesmerized.

When receiving the book, Wunue adjusted his clothes and knelt, respectfully receiving it with both hands.

Qing was also startled and returned the gesture, making the moment truly solemn.

"Here you go. A Great Revitalization Pill. I only have one on me right now, in case of an emergency. I will send the rest to the Divine Maiden Sect through a messenger later."

"Hehe, you shouldn't have……"

As she said so, Qing diligently pocketed the pill. Then, a thought occurred to her.

"Ah, that's right. I heard that women are not allowed in Shaolin……"

"Do you wish to see Shaolin? But the precepts are strict, so even I cannot do anything about that."

Wunue wore an apologetic expression.

But what couldn't be done, couldn't be done.

Even for such a great benefactor, he couldn't break Shaolin's greatest precept just to accommodate her.

"No, that's not it. Then, can women not see the Absolute Sword Wall either?"

"Ah, you wish to see the Absolute Sword Wall. That is not a problem. The Celestial Martial Emperor placed it on the Southern Peak, separate from the temple, precisely with such intentions in mind. Come and ask me anytime. I will guide you."

Then, Wunue's expression brightened.

Since Shaolin was located on the North Peak of Mount Song, women were allowed to enter the South Peak.

In the first place, it was impossible to ban women from the entire vast expanse of Mount Song.

"Thank you for your consideration."

"No need. It is a legacy that should be shown to any promising talent with the spirit of the Orthodox Faction."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The Wulin Alliance's Military Advisor Department was a sub-department where the brains of the Murim Alliance gathered.

Originally, a Military Advisor was someone who led troops with tactics and strategy, but since Wulin was so peaceful these days, there was no such need.

So, they were just the actual paperwork handlers who ran the Wulin Alliance.

The head of the Military Advisor Department was the Chief Military Advisor of the Wulin Alliance.

Below the Chief Military Advisor were the Assistant Military Advisor and the Deputy Military Advisor, and below the Deputy Military Advisor were the positions of Deputy Assistant Military Advisor and Military Secretary.

And the current Deputy Assistant Military Advisor of the Wulin Alliance was the famous Jinang Hyeonhwa, Sama Chunbong.

Jinan Hyeonhwa meant 'Wise Pouch, Intelligent Flower'.

She was called the Wise Pouch because it was said that all the wisdom in the world was contained within her.

According to the evaluations of the Dragon-Phoenix Assembly, she was a bit too arrogant, making her a rather unpleasant person to deal with for some factions.

And her name was a bit old-fashioned.

However, regardless of the politics of the Dragon-Phoenix Assembly, the evaluation of the Wulin Alliance's Military Advisor Department was similar.

They often complained that she was too arrogant. However, the difference was that everyone in the Military Advisor Department treated Sama Chunbong like a daughter or a younger sister.
Of course, they still thought her name was a bit old-fashioned.

Sama Chunbong did not acknowledge this evaluation of being arrogant, because she had never been arrogant in her life.

Sama Chunbong was wronged.

It wasn't arrogance, but rather an extraordinary brilliance that inevitably leaked out because she was simply too outstanding.

Yes, that's right, it was just the fragment of a genius!

Hmph, how can mere mortals possibly understand a genius?

I might as well bear with it, I suppose.

Thus, today, the young, ultra-genius, ultra-beauty (in her opinion) Sama Chunbong, as the next youngest Chief Military Advisor of the Wulin Alliance (in her opinion), was very diligently doing things she wasn't even asked to do.

The investigation of the series of murders in Kaifeng caused by the Lone Star's consecutive self-destructions was one of them.

In Sama Chunbong's opinion, this was clearly a very wicked conspiracy by some kind of hidden force trying to plunge the peaceful Wulin world into despair!

The Deputy Military Advisor of the Wulin Alliance called out to Sama Chunbong, who was lost in thought.

"Hey, Chunbong. Did you finish rearranging the seating for the finals?"

Then, Sama Chunbong suddenly turned her head.

"Oh my. Is that a butterfly?"

"I asked if you finished it……"

"This year's summer will be scorching. Since the butterfly is already so weak, it means the heat wave will plunge the world into despair. What should we do about this?"

"Sigh. That. Miss Sama. Did you finish rearranging the seating for the finals?"

Only then did Sama Chunbong seem to hear him.

"Oh my. Do you think I would spend even a moment on such trivial tasks? I finished it already and put it up, so check it yourself."

"Is that so? If you're done with your work, why don't you adjust the odds for the betting pool? Or just go home. Why are you just sitting there?"

"Deputy Military Advisor. I'm trying to find out more about the series of murders in Kaifeng."

"I told you to drop that case. Do you have nothing better to do? Then go to the Dragon-Phoenix Assembly and hang out with people your age. Huh? Make some friends. Aren't you being bullied?"

"Hmph. It's just that I choose not to associate with them. How can a phoenix mingle with sparrows?"

"That's called elitism."

"Elitism? I'm a very down-to-earth genius without any elitism. Of course, the ignorant might not recognize it."

At that, the Deputy Military Advisor sighed deeply.

"Chunbong-"

"Oh my, look at those leaves already withering. This summer will be truly harsh."

"Miss Sama."

"Yes?"

"If you have nothing to do, go wash your feet and sleep."

At that, Sama Chunbong yelled.

"Aigoo, I'm telling you I'm going to investigate the series of murders in Kaifeng! This very body! Hyeonhwa Sama, the Chief Military Advisor! With an unparalleled mind!"

"I don't like every word you just said. And the Chief Military Advisor is perfectly fine, so saying that makes you sound like a traitor."

"I don't know what you're talking about."

"Anyway, we're done with that case. What good would it do to dig into it when the Wulin Tournament is in full swing? It's already been neatly concluded that it was the unlimited self-destruction of the Queen of Gu."

"But! Some hidden force in the shadows!"

"It was revealed to be the Blood Cult……"

"A grand conspiracy!"

"They discarded their undercover agent and withdrew……"

"This is an opportunity to solve it and elevate the name of Hyeonhwa Sama, the Chief Military Advisor!"

"Yeah. You only move for your own benefit. Hmph. Anyway, the Chief Military Advisor has already received the Alliance Leader's approval on this matter. Drop it."
Honestly, the Deputy Military Advisor didn't expect much even as he said this. After all, she was someone who never listened to others.

"Hmph. Investigating in my personal time should be no problem, right? I've already caught a lead, so I'll solve this case in a spectacular, brilliant, and wise way!"

"No, it's already solved. Huh? Wait, you caught a lead?"

Then, Sama Chunbong declared triumphantly with a smug smile.

"Of course! Just wait and see! I will uncover every detail of this incident thoroughly, in detail, and beautifully!"

She wouldn't listen even if he tried to stop her.

The Deputy Military Advisor just sighed deeply.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Black Mark Society Head, Jang Eunche, gritted his teeth at the mysterious imposter Un Yeonyoung, but he couldn't properly express his resentment.

Because bad news kept coming in one after another.

"This is bullshit! What do you mean, White Mark?! Are those Demonic Cult bastards completely insane?! What kind of prank is this?!"

All the Black Mark branches in the north and west of Gansu Province had been annihilated, and some bastards called White Mark had taken their place.

The logic of White Mark was simple.

White Mark protects merchants.

White Mark also protects customers.

White Mark kills the scum of humanity.

Human traffickers, black market dealers, and those involved in the production, processing, and distribution of human flesh were caught, stripped naked, and tied up in the main streets.

And on their bodies, their crimes were inscribed, such as 'butcher', 'black market dealer', 'cannibal', 'assassin', and so on.

Passersby would throw stones for fun, or brand them with fire, or beat them with clubs.

As a result, the black market in the northwestern region of Zhongyuan was on the verge of extinction.

'Those bastards who dare to touch the Black Mark and invade our territory!'

He tried to push them back with money, but suddenly, a bunch of renowned Demonic Cult experts showed up and annihilated them without even being able to take down a single flag.

In other words, it was the work of the Demonic Cult!

Well, they didn't seem to have any intention of hiding it in the first place.

Now, the Black Mark had been annihilated in the southeast and northwest regions of Zhongyuan.

"Without the black market, what's the point of customers coming in the first place! If you want to make it an ordinary marketplace, who would bother to visit White Mark when they could just go to the local market!"

Jang Eunche yelled.

The reason the black market was thriving was that it was a place where one could trade goods that were hard to find or banned by the government.

That was what he thought, but…

"It is said to be unexpectedly thriving. They say that even martial artists must be polite to customers in the territory of the White Market, and that the Heavenly Demon Divine Cult will absolutely not forgive any who disobey, so merchants are flocking there, and customers are following suit."

White Mark protects merchants.

White Mark also protects customers.

They would kill the scum of humanity, which included those who took goods and ran or swindlers.

They guaranteed safe and comfortable transactions as mediators between both parties, so whether it was customers gathering that drew in merchants, or merchants gathering that drew in customers, either way, business was booming.

"Fuck! Why! Why me! Why! Why is this happening to me! Why!"

"It seems you should lie low and hide for now. There are rumors that assassins are looking for the Society Head these days……"

A request could be successful or it could fail.

However, a request that could never be successful from the start, one that drove the requester into a deathtrap, was akin to fraud.

And Jang Eunche had already made a name for himself on the assassins' hit list.

"Ha. Fuck. You think I'll sink like this? I was thrown into the back alleys and clawed my way up to become the Black Mark Society Head. I won't die like this. Ha. I'll lay low for now, but just you wait and see. Just wait until I get an opportunity. Just."

Jang Eunche muttered grimly.

Of course, no one could know whether that opportunity would come or not.
