\chapter{The Appearance of the Divine Dragon (6)}

"Young Lady Ximen, you are so, so pretty. Goodness. How can someone be so……" 

Upon seeing Qing, Gongson Yeyeah could not take her eyes off of her. She fired a gaze full of envy, so much so that it made Qing feel embarrassed instead. 

"What's with the praise? Why are you bare-faced?" 

"Well, since martial artists are stepping forward in front of the people, putting on makeup seems a bit too girly. Ah, I'm not talking about you, Young Lady Ximen. It's just that you're so pretty, so it's different. But for someone as plain as me to put on makeup, I'll just be ridiculed……"

"Hey, is it wrong for martial artists to wear makeup? Imitating male martial artists is not the way for female martial artists. My teacher told me that." 

Qing delivered the teachings of Ximen Surin, explaining the reasons for the beauty of female martial art Masters. 

"To think you would call me the representative of female martial art Masters. Those are far too kind words……"

"Why? If it's you, I think you're already the best among the young Masters. Of course, I do exist, so, ahem, that's a pity for you. Now. Look at me. It's good that I brought this just in case. Just a moment! Just one moment!"

Having received the teachings of Ximen Surin on how to be a beautiful person, Qing was already a master of tying her hair and applying makeup. However, unlike her hair, which she always paid attention to and thus had naturally mastered, she did not put on makeup often. 

In Zhongyuan, there existed as many makeup methods as there were styles of clothing. The type of makeup Qing preferred was quite classic.

Sumi. Eyebrows are thin and slightly frowned. And, the eyelids were thickly emphasized to enlarge the eyes. In addition, a light blush was applied only to the lower part of the lower eyelid, a style called weeping makeup, to create a rosy look after crying. The blush on the cheeks was faint. And then the lips, but she did not prefer the style of clearly drawing the center in the shape of a cherry, so she spread it out to the sides, creating a natural tone that gradually faded towards the corners of the mouth.

"Awww, so pretty. I'm going to fall for you."

"Even if you say such a thing, Young Lady Ximen……"

"Well, I'm just riding on the coattails of the Fairy Arts. You're already pretty even without the Fairy Arts, so how about learning one? It's a shame, you know? Such a nice canvas."

"Later, later……" 

Gongson Yeyeah, with only her eyes, cheeks, and lips colored, somehow had her entire face flushed red as she bowed her head. 

At that moment, the staff of the Wulin Alliance urged the two. 

"Are you not ready yet?"

"Ah! We're all set now! Let's go, Yeh."

"Yes, yesss." 

And then, she walked out, her arms and legs stiff as if their joints had frozen. Why is she so stiff again? Qing lightly took Gongson Yeyeah's hand.

"What's wrong? Are you nervous? Why are you nervous when we're not even going to swing swords?"

"Aren't you nervous, Young Lady Ximen? I'm, um, I'm not really someone who people like, you know?" 

"So what? I'm also disgusted by those people out there, you know? But what does it matter if people we don't know and will never know in the future like us or not? Isn't it enough if our friends like us?" 

"Then! I, um, that's not it."

Gongson Yeyeah suddenly raised her voice, then made her voice as small as an ant's. 

"Why? Why are you stopping mid-sentence? Have you heard of this? There are two ways to make a person angry. One is to stop in the middle of a sentence."

At that, Gongson Yeyeah waited for Qing's next words quietly. However, Qing just smiled, causing Gongson Yeyeah to tilt her head in wonder.

"See. It's like this when someone stops mid-sentence. So, what were you trying to say? Why are you hiding things from our relationship?"

"Ah……. That's, I…… You have many friends, Young Lady Ximen, so I'm not really that special and I thought you might just be hanging out with me like an acquaintance……"

Once again, the volume of the latter part of her words decreased drastically. 

"What are you saying? Aren't we friends who have shared a bed? You're one of my closest friends, along with Nana." 

"Ah, then it's just the two of us……"

"Ah, there's also Jangmyeong and sworn sister."

At that, Gongson Yeyeah's expression turned sorrowful.

"Huh? What's wrong?"

"It's nothing. One-half, no, one-fourth, no, that's not it either. Um, Young Lady Ximen? Perhaps, how many times have you done that with others? No! It's nothing! We're late, so shouldn't we hurry? Since they were waiting for us."

"Ah. That's true."

Although her behavior was strange, her movements became natural, so it seemed that her tension had eased a bit.

Qing held Gongson Yeyeah's hand tightly and climbed the stairs leading to the stage. 

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The spectators of the martial arts competition were not so much anticipating but rather harboring a grudge. Just how pretty is she that even a Shaolin Monk made such a fuss and acted disgracefully?

However, most believed that he was still a young monk, unable to resist even a slight brush of a woman's skirt. Moreover, she had covered her face, saying that her beauty was a distraction (Qing had never said such a thing). How great a face could she have to go that far? They scoffed, saying that she must be afraid that everyone would surrender upon seeing her face without even needing to use their weapons. 

Furthermore, even if she were a true beauty, was there a need to endure being called the Ugly Masked Swordswoman, pockmarked, or having a face so hideous that it made one vomit up their food? 

Thus, when Qing ascended the stage, the people merely nodded in unison.

I see. Even if it wasn't a young monk, even if a highly virtuous monk had come, he would have made a fuss. 

Indeed. It would be right to cover such a face. How can one even think of touching such a beauty?

Indeed. How can you insult a beauty of such a level by calling her ugly? She'd just ignore you.

And so, they were engrossed in their own descriptions of Qing's beauty.

After all, boasting about this experience would be a great conversation starter.

The level of entertainment in the primitive and uncivilized ancient China was about throwing stones at each other in village battles and looting warehouses and women. If not that, it was about spreading or listening to tales of heroism.

So, they were preparing to brag about how they had seen a beauty under the heavens and what she was like.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The fact that the peerless art under the heavens, the Nine Arts of the Buddha's Palm, had been lost was known throughout the martial world. 

In fact, this was quite a strange occurrence. 

Usually, when a peerless art was lost, it meant that the sect had lost its power. As such, even if it was the Shaolin Sect, which had countless Divine Arts that Qing described as being able to just pick and choose violet-grade martial arts, it was not something to be easily revealed to others. 

Ximen Surin simply stated that the Nine Arts of the Buddha's Palm had disappeared due to the absence of a successor, but she was a female activist with a grudge against Shaolin (as the greatest sect in Zhongyuan was men-only).

Although it was an obvious fact whether it was true or false, there was also a sad story behind it.

In the past, there was a great flood that could overturn the world. The Shaolin Temple, located at the top of a mountain, suffered no harm, but the damage suffered by the commoners below was indescribable. Thus, the Shaolin Temple actively engaged in the salvation of the people. They opened wide the massive warehouses, which had been filled by alms, land, and sales of elixirs, and provided relief. The warehouses seemed to be endless as they kept on giving, enough to greatly alleviate the suffering of the people. 

As such, everyone in the world praised the benevolence of the Shaolin Temple.

And the Emperor felt a sense of displeasure.

How could those lowly monks receive praise when the Emperor, who ruled the center of the world (Zhongyuan) in accordance with the will of Heaven, existed?

During the relief efforts, he played around, saying that natural disasters were the will of Heaven and that the Emperor should not go against it. Then, when Shaolin provided relief, he felt that they had harbored malicious intent and sent cannons their way.

Meanwhile, the Nine Arts of the Buddha's Palm naturally had a Secret Manual. There was even a backup copy made just in case. The Secret Manual was kept in the Scripture Depository, the most famous martial arts library in the world, along with other Divine Arts. And the backup copy was kept in the Sutra Depository in preparation for any unforeseen disasters. 

It was just that the popularity of the Hundred Paces Divine Fist was higher than the Nine Arts of the Buddha's Palm, something even the monks of Shaolin could not help.

If one wanted to learn a long-range palm strike, it was easier to learn the Hundred Paces Divine Fist, which also went well with the other supreme techniques of Shaolin.

Since there was also the Great Diamond Palm and the Primordial Palm, it wasn't a great choice as an Inner Qi Cultivation Method either.

So, they just kept the Secret Manual in the Scripture Depository and made a copy just in case, thinking someone might want to learn it someday. After all, it was impossible to force someone to learn and develop it. If it wasn't meant to be, then so be it. How could the Shaolin Sect, following the teachings of Buddha, force someone to learn a martial art against their will?

As such, they thought someone might learn it if their destiny allowed it to happen, but then the government's cannons burned down the Scripture Depository. The backup library, the Sutra Depository, also burned down.

In the end, their destiny was completely burned away.

They could only soothe their bitter hearts by thinking that it was never meant to be.

But now, that destiny had been revived.

"We must retrieve the Divine Arts!"

"No matter the cost, is it not the origin of the Buddhist Law that we must retrieve?!" 

"This must be investigated thoroughly! How can a supreme technique that must not be passed on to outsiders be used by someone outside of our sect?!"

"Send someone to the Divine Maiden Sect immediately……, no, I will go myself."

The martial monks of Shaolin raised their voices.

Great Master Wunue clicked his tongue.

"I know the Godmother's personality. If the Divine Arts were at the Divine Maiden Sect, she would have already returned it and taken all the Great Rejuvenation Pills. Since she didn't, it means that child must have personally encountered the fortuitous opportunity."

"But isn't she the Grand Sect Leader of a sect? How could she not take such Divine Arts-."

"I'm telling you, she's not someone who would hide it even if she had it. Anyway, about those who don't know. Hmm. It would indeed be right to retrieve a lost heirloom. However, would they be convinced if we just claimed it as ours after losing it over two hundred years ago? Yes, what should we give? What should be the price for the Divine Arts? If we are not careful, we will be committing the error of putting a price on something that is priceless."

After all, something priceless was invaluable because it had no price. On the other hand, if it was given a price, its solemn nature would be diminished. If it was returned for ten thousand gold coins, then it would just become a martial art worth ten thousand gold coins.

"How about Great Rejuvenation Pills? If we offer all the quantity we have in the Pill Hall right now."

"Aiyo. We would be selling Great Rejuvenation Pills, so that is also ridiculous. Are we going to say we will exchange it for merely ten Great Rejuvenation Pills?"

"Then, how about Divine Arts for Divine Arts? If we just receive a promise not to pass it on……"

"How can you say to pass on the essence of this sect to an outsider, Great Master? Please speak sense."

"What?! Are you saying everything I say is nonsense, you baldy? Then do you have something to offer? Or are you going to attend for fifty years as penance to get it back?"

"Hmph."

Thus, they started discussing among themselves, bringing up the Cleansing Marrow Sutra, the Infallible Vajra, the Nine Cycles of Yeon, the Divine Fist of One Hundred Lotuses, and whether they should give one of those.

At that, Great Master Mahak clicked his tongue.

"Aigo. You foolish fools. Now I see you are not monks but mere merchants. Since you are just thinking of setting a price and buying it, why did you even enter a temple? You have all gathered here as talents who will become great merchants. Tsk tsk."

"Then, what should we do?"

"We must buy with grace, not with price. Give them all the Great Rejuvenation Pills, Lesser Rejuvenation Pills, and Divine Arts. The world will say that Shaolin is indeed different, and those who have our goods will return them, expecting grace. Isn't that so?"

"But if it gets leaked somehow."

"Then, that will be the day when the One Hundred and Eight Arhats descend to the mortal world all at once. That will also be a great lesson to the world, showing what happens when you try to take advantage of Shaolin's grace. But that's something to worry about only if it actually gets leaked, so why worry and fret about it now?"

At that, some of the monks exclaimed in admiration, seemingly enlightened, while others still wore dissatisfied expressions, unable to hide their displeased and sour faces. 

However, if Wunue said so, then so it was.

"If you are still worried, let us see how that child is first. If she is frivolous and greedy, then giving her the Divine Arts is not an option. But if that is the case, then she will likely be swayed by material goods anyway." 