\chapter{The Appearance of the Divine Dragon (1)}

The Wulin Alliance was in an uproar, though they tried to keep it under
wraps.

Several mid to low-ranking officials, including secretaries and
assessors, had died within the Wulin Alliance Headquarters.

The victims had suddenly complained of abdominal pain, collapsed,
convulsed, and ultimately died.

And upon hearing the autopsy results, Jo Hyeonryang clutched his head
in agony.

"Poison? What are you talking about?"

"The internal organs were severely damaged by a potent poison that
suddenly erupted. The gallbladder and liver were unusually clear in
color. Moreover, there are reports that there have been victims in the
government as well."

"Ugh. So?"

"The Military Strategy Department believes that some group spread
poison in Kaifeng for a specific purpose, and upon achieving their goal
or reaching a point of no return, they disposed of the entire group and
left."

A point of no return. Jo Hyeonryang thought.

It seems the Military Strategy Department was indeed fond of using
fanciful language for no reason.

"Didn't the guests from the Tang Clan arrive? They're experts in that
field, so why not ask for their cooperation?"

"Isn't it something that could expose the Alliance's weaknesses? For
now, we are investigating whether there has been any misconduct
among the victims due to the subjugation through poison."

"Hmm. I see."

Jo Hyeonryang nodded.

He wondered if there was a need to report if they were going to handle
everything themselves.

But this was the fate of the Wulin Alliance Leader.

The staff handled the practical work, but the leader had to know
everything that happened within the Alliance.

"And here are the results of this year's Grand Assembly. Please review
them thoroughly and give your approval. If you just stamp it
carelessly like last time and then claim you didn't authorize it, we will
be in a difficult position."

If you're going to be like that, why don't you be the Alliance Leader?

Jo Hyeonryang merely sighed deeply.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The fervor of the Martial Arts Tournament was reaching its peak.

With various events also coming to a close, it was time to announce the
results of the Grand Assembly before the semi-final matches of the
Hidden Dragon Sparring Tournament on the shipboard sparring stage.

It was the collective will of the (orthodox) martial artists, with even
small local martial schools having a vote.

Jo Hyeonryang, dressed almost like an immortal, announced the
future official activities of the Wulin Alliance with a powerful voice
infused with Inner Qi.

First, there was news of support for the orthodox martial schools in
the southeastern regions of Zhongyuan, including Yangzhou and
Jiaozhou.

It was to help them break free from the pressure of the Demonic
Alliance, which had been suppressing the region.

The establishment of a new branch of the Wulin Alliance in Hunan was
an extension of this, as it was the optimal location to quickly reach
anywhere in Yangzhou or Jiaozhou.

However, what excited everyone the most was the revival of the
Righteous Assembly Martial Academy.

In simple terms, the Righteous Assembly Martial Academy was a
non-regular training institution of the Wulin Alliance.

The idea was to send talented young boys and girls, and the Alliance
would train them into masters.

With generous support including (family-grade) secret arts from the
Nine Great Sects and Ten Great Clans, as well as (low-grade) elixirs, it
was said that every time the academy opened, future masters would
emerge in droves.

In truth, it wasn't a particularly appealing option for famous factions.

If they had renowned Divine Arts and a well-established system for
training disciples, there was no need to send their talented individuals
to be trained by the Wulin Alliance.

However, for the smaller martial schools and unknown young
individuals who wished to join the ranks of orthodox martial artists, it
was truly a gateway to success, a once-in-a-lifetime opportunity to rise
from obscurity.

-Ooooooh!! Waaaaah!!

Amidst the heated atmosphere, Qing listened to the cheers that could
be clearly heard even from beyond the waiting room's porthole.

"What's going on? Did some famous restaurant start handing out
all-you-can-eat vouchers or something?"

"Seriously. Everything always comes back to food with you."

"What else could make them so excited? Unless the Alliance Leader
announced he's treating everyone to a feast today."

Peng Daesan, who was waiting for his match, chuckled.

The two semi-final matches were Gongson Yoyeh versus Peng Daesan,
and Wolbong versus Ximen Qing.

In the end, despite everything, it came down to the individuals with the
highest realms.

"San. What are we going to eat after the match? Anyway, it's either San
or Yeh who's going to win, so today, I'm treating. The winner gets a
celebratory drink and the loser gets a consolation drink. How about
Sahong Spring Wine? I heard it's a rising star among breweries these
days."

"Aren't you even nervous? Hmm. If you lose, it might end up being your
consolation drink."

"No way. There is no way that this Transcendent Peak Ximen Qing will
lose in a competition where a bunch of kids are just playing around."

At that, Peng Daesan raised the corner of his mouth and asked.

"By the way, who are you rooting for? Me or Young Lady Gongson?"

"What? How childish. San. Were you the type to ask 'Do you like mom
more or dad more'?"

"It would be awkward to say you like both. So, who are you rooting
for?"

"Hmm."

Qing rubbed her chin, pretending to think seriously, before finally
giving an answer.

"I guess I have to root for San. After all, we've known each other longer."

"Are you sure? If Young Lady Gongson were here, I think you'd give a
different answer."

"No way. Based on our sparring results, if San makes it to the finals, it's
an automatic win. As for Yeh, she's, like, kind of tricky to deal with. And
it seems like she hasn't even revealed her true skills yet, hasn't she?"

Peng Daesan's eyebrows twitched.

It basically meant that Qing was rooting for him because he was easier
to deal with.

"Do people usually say that kind of thing to someone's face?"

"Hmph. If you don't like it, then win and come up to the finals."

"Ha. You too. Don't underestimate the martial arts of Shaolin, or you'll
be in for a surprise. If you lose, don't worry too much. I'll treat you to
drinks until you're completely wasted."

"Hmm. I can't tell if that's an insult or a kind word."

As Qing tilted her head…

Finally, it was Peng Daesan's turn.

Peng Daesan got up and headed out of the waiting room, but then he
paused, looked back, and spoke.

"Win and come up. Shouldn't we have a proper match in the finals?"

Then, with his ears slightly red, he quickly left.

Qing instantly intuited the outcome of the match.

When you say something like that, you're bound to lose. It's a universal
constant.

And as a result of that cosmic inevitability, it actually happened.

Since Qing had already anticipated it, she wasn't particularly surprised.
However, she just found another thing to tease him about and her eyes
sparkled.

And then, it was Qing's turn.

As she confidently walked through the now-familiar passageway on
the ship, she was about to jump onto the sparring stage.

When suddenly, a massive cheer, loud enough to vibrate the thick
ceiling and the floor of the shipboard sparring stage, came rushing in.

In Wulin, the status of the Shaolin Sect could be described in one
word.

宗主. Taisan. Mount Tai.

It was said that all martial arts originated from Shaolin.

As such, to ordinary people who knew little about martial arts, Shaolin
was an idol, practically synonymous with Wulin itself.

Moreover, the Greatest Under Heaven had emerged from Shaolin.

And since a young disciple who was continuing that lineage had been
advancing rapidly with consecutive victories in the Hidden Dragon
Sparring Tournament, it was only natural for everyone to be excited.

There were already many who were enthusiastically proclaiming that
the next Greatest Under Heaven was making his momentous debut in
Wulin.

It was almost as if the winner of the sparring tournament had already
been decided.

Riding on this fervor, when Monk Wolbong soared up and landed with a
thud, the resulting cheers truly shook the heavens.

And as Wolbong performed the Shaolin Sect's unique greeting in all
directions, the cheers grew even louder.

It was a form of greeting called the half-palm salute.

Once upon a time, a highly virtuous monk named Huike asked Bodhidharma for his teachings and, as a sign of his sincerity, cut off one of his arms and offered it as a tuition fee.

When Bodhidharma saw the severed arm, he thought, 'This one's a real
psycho', and accepted him as a disciple. Or something like that.

A full prostration originally involved putting one's palms together, but
since Great Master Huike only had one arm, he could only put half a
palm forward.

It's half a palm because it's only half, hence the name, half-palm.

However, the cheers were a bit too long.

It was because the spectators, excited to witness the moment when the
future Greatest Under Heaven spread his wings, could not contain their
excitement.

As a result, Monk Wolbong raised his half-palm once again.

Then, without any regard for their own throats, the spectators raised
their voices even higher.

Seeing this, Ximen Surin frowned.

Originally, at official events, when one person made an appearance
and received cheers, it was basic etiquette for the next person to wait
until the cheering subsided.

However, if the cheering went on for too long, the next person had to
wait indefinitely, so it was also their duty to request for it to quiet
down at an appropriate level.

Thus, Ximen Surin could not help but click her tongue.

That young monk is quite the sly one, isn't he?

Of course, one could understand that a monk who had only trained in
the mountains without ever getting his name out there would be
intoxicated by the public's enthusiasm.

But for a martial artist of Shaolin, whose focus was on maintaining an
unwavering, steadfast heart, he was still far from being disciplined.
Ximen Surin glared at the head seat, her discomfort unconcealed.

As expected, the Great Master Wu Xue, also known as the Divine Monk
and the current Greatest Under Heaven, was frowning, unable to hide
his embarrassment.

Seeing that, Ximen Surin felt a little better.

It seems he has taught his disciple martial arts well, but not the
principles of Buddhism.

Finally, the host had to step in, waving both hands and asking for
silence.

And only then, my lovely disciple made her entrance, walking as
prettily as a fairy-

-Wooooo. It's the Ugly Sword Demoness.

Ximen Surin clenched her fist tightly.

There was little response, making it practically silent compared to the
thunderous cheers that had shaken the sparring stage earlier.

It was a stark contrast even to when the Gongson child had appeared
earlier.

Of course, the Gongson child was pretty, even if modest, and since her
opponent was the Jade Qilin, the cheers were even more overwhelming.

My disciple must have been cursed with an ugly face since she's
wearing a veil, huh? That must be it. That must be why the crowd is
reacting like this.

Ximen Surin, who had already experienced the treatment of women in
Jianghu, was worried that her disciple might be hurt even before the
match began.

Qing didn't particularly care.

She was just thinking, 'Shaolin is really popular, huh?', as she waited
nonchalantly.

In fact, even in the past when Qing didn't know anything about Wulin
or martial arts, she knew that the Shaolin Sect was composed of
martial artist monks. To that extent, it was common knowledge to the
point where it was strange if someone didn't know about it.

But then, where did this common knowledge come from? There was no
way to know if one thought about it.

"This girl is Ximen Qing."

"Amitabha. I am Wolbong of Shaolin."

Only then did Qing get a closer look at Wolbong.

Wolbong had never shown his face anywhere except for the sparring
tournament, acting haughtily, and Qing, who only hung out with her
friends at the Cheonmu Pavilion, had only seen him from afar in the
audience.

Thus, Qing thought as she looked at Wolbong.

Hm. But… He looks a bit old, doesn't he?

Is he really a Hidden Dragon? I guess so?

At a glance, he looked to be in his mid-thirties, so she thought it was a
bit much for him to be in a competition for rising stars.

But then again, Qing wasn't in a position to be too proud of herself
either.

Qing was participating, claiming to be twenty this year, so she knew
very well that one could just lie about their age.

If he knew, Wolbong would have felt wronged.

Because Wolbong was twenty-seven this year, a young man in his prime.
Moreover, the young disciples of Shaolin tended to age a bit faster
since they were made to rigorously train their external martial arts
from a young age.

Among them, Wolbong was just a bit more severe.

Whether he knew of Qing's impolite thoughts or not, Wolbong
continued with his half-palm salute.

"I shall yield the first move to the almsgiver."

"I won't refuse. Here. I. Go!"

Following that, Qing stepped forward powerfully. 