\chapter{The Appearance of the Divine Dragon (12)}

There is a great figure who cannot be considered a part of the
uncivilized Zhongyuan.

The first and greatest historian of Zhongyuan, and a great figure
who can be confidently named as the greatest historian in the entire
world and throughout all ages, Sima Qian.

Sima Qian was a historian of an ancient civilization who accomplished
the enormous feat of recording the history of an era as an individual.

At the same time, he was faithful to his duty as a scribe.

He vividly described the lives of both those in power and the common
people, striving to remain as objective as possible, setting aside
personal grudges.

Of course, he seemed to harbor a deep resentment towards Emperor
Wu of Han, who had him castrated, but considering he was made a
eunuch, such resentment was understandable.

He was noble as a scribe, fundamentally different from the human
trash back in Qing's homeland who deserved to be burned to ashes.

Of course, comparing a toxic, irredeemable waste with a human being
would naturally lead to a fundamental difference.

At any rate, this masterpiece by Sima Qian was called the 'Shiji', or
'Records of the Grand Historian'. And because the lazy people of the
Zhongyuan thought even four letters were too long, they shortened
it to 'Records'.

According to these records, 'A scholar dies for one who recognizes
his worth'.

Therefore, the debt of gratitude that the Ronin felt towards Qing was
not something that could be expressed in just two mere words.

Ronin were essentially consumables.

They were consumables that could be bought with money, used to
shield from swords at the front lines of battle, analyze enemy strength,
and breach traps.

What? You're hurt? Then we'll just replace you with another one.

What? You're dying? Then we'll just replace you with another one.

What? You're dead? Too bad. We'll just replace you with another one.

Not only was their treatment harsh, but the perception of them was
even harsher.

If they were employed, they were Ronin; if not, they were bandits.

They acted like they were best friends, but if they met on opposite sides,
they would clash swords without hesitation. In reality, they were
cold-blooded individuals who just pretended to be close to exploit
each other.

The part about being bandits was not entirely untrue, but for
independent martial artists who prided themselves on living with a
sense of righteousness, it was just an unfair accusation.

Moreover, if they fought for money and pretended to be on the same
side just because they knew each other (which they often did), they
would be criticized for lacking a moral code and loyalty.

Then, Qing appeared.

To the Ronin, Qing did not deny their shameful background as Ronin.

Instead, she comforted, encouraged, and affirmed them.

Their efforts to live righteously despite their difficult backgrounds were
acknowledged.

And this was not just empty words, for she proved it by risking her own
life.

It was the first affirmation the Ronin had ever received in their lives,
an acknowledgment that their lives had not been in vain.

Therefore, the Ronin felt they could die for Qing at this very moment.

Of course, their feelings might change in the face of death, so their
future feelings could not be guaranteed.

As such, the stories told by the Ronin were akin to epic poems,
praising Qing to the high heavens.

The virtuous Ronin had fallen for the insidious tricks of the vile Blood
Cult. As a result, they did not hesitate to use the despicable method of
the Submerging Venom Pill before swallowing even the poisons
themselves.

Then, the wise and radiant Great Hero Ximen Qing saw through this
and said, 'It is truly unfortunate that you could not resist such a brief
temptation, but do not worry. This Ximen Qing will solve everything'.

She then tracked the Blood Cult alone to a hidden cave deep
underground. With a single swing of her sword, she separated the
bones and flesh of the Blood Cult warriors. And when she pointed her
finger and commanded them to die, they could not help but commit
suicide in awe of her majesty.

Finally, she eliminated the wicked leader of the Blood Cult (though
the Blood Demon would have been bewildered to hear this) and used
her brilliant wisdom to remove the poisons.

Meanwhile, Moyong Juxi was conspicuously absent from this story,
because the Ronin had no knowledge of her at all.

After all, these people had never even set foot in the underground.

After hearing the full story, Sama Chunbong thought.

They call themselves Ronin, but all they do is lie through their teeth.

However, with her sharp mind, she discerned the truth from the lies.

The conclusion she reached was that Qing had grasped the situation
and sought help from her master to resolve it.

If it was the Zenith Among Women, a mere independent unit of the
Blood Cult, even the Blood Cult Army, would be nothing more than
insignificant bug breeders with no martial prowess to speak of.

At this, Sama Chunbong felt both a sense of crisis and exhilaration.

The crisis was that a powerful rival had appeared, threatening the
position of the next generation's greatest talent.

And the exhilaration was that finally, a proper rival had appeared for
this extraordinarily talented and peerlessly beautiful woman.

A worthy rival was essential for a true genius.

After all, a rival was also the greatest source of understanding.

It was a joyous occasion to finally have a great intellect appear who
could understand her, unlike the current generation of commoners
who were practically a different species.

Unfortunately, she was born in the same era as the great Sama
Rang.

Anyway, Sama Chunbong promptly wrote a report and submitted it.

And that report went from the Chief Strategist's hands to the leader of
the alliance, the Martial Alliance Leader.

Thus, Jo Hyeonryang exclaimed.

"Surin has done it again. No, she should have told me if she did. Why
keep quiet about such an achievement that should be widely
announced to the world?"

"Perhaps she did it for the face of the Alliance? It wouldn't look good
for the world to know that the Blood Cult was operating while the
martial arts tournament was being held."

"Hmm."

Jo Hyeonryang replied brieﬂy.

However, unlike what the Chief Strategist had interpreted, the 'Hmm'
here was not an affirmation but a complete negation.

How could the Female Mad Dog possibly do such a thing?

She was definitely not someone who cared about the face of the
Alliance.

She would have surely boasted to the whole world, 'Look. In the end,
it's always a woman who does the great deeds. Look at this while all
you men do is play around,' and behaved like the Female Mad Dog she
was known to be.

However, Jo Hyeonryang did not need to dwell on why she was acting
so strangely.

"That? My disciple did all of that. I went down with her because I was
worried she might be in danger, but I just ended up killing a few
small fries."

"The disciple, Ximen Qing, did? Even if the Blood Cult Army is not a
frontline combat unit, the Mad Demon of the Earthly Curses was not an
easy opponent."

"Do you think I would lie about something like this?"

Jo Hyeonryang nodded.

The Female Mad Dog was a mad dog, but she did not lie. She was
always an infinitely frank person.

"And don't worry, she also killed the leader, so it was a complete and
thorough job."

"She killed the leader too? You must have dealt with the leader, right?"

"No. When I woke up, my disciple held out his head to me. It was the
Blood Wheel Demonic Devil."

Of course, she did not lie.

It was just that Ximen Surin knew that not lying could be a powerful
weapon.

"The Blood Wheel Demonic Devil! Then, Ximen Qing killed the Blood
Wheel Demonic Devil? Is that true?"

Ximen Surin just smiled silently.

At that, Jo Hyeonryang slapped his knee.

"My goodness, what a blessing, what a blessing. She is truly a new star
of the martial world, a Divine Dragon. No, how do you raise a disciple
to become like that? I saw her, and not only was her skill exceptional,
but she was also full of integrity, polite, and cheerful. Haaa. I'm so
envious."

"Did I raise her? She was like that from the beginning. It's commendable
that I didn't have to do anything."

Ximen Surin was being modest, but her face was beaming.

Jo Hyeonryang couldn't hide his envy.

"How did you manage her character? Please, I need to manage the
heir of the Jo Clan right now. Tell me your secret. Huh?"

"When I saw that child, the part I liked the most was her character, so I
didn't have to touch it."

"Come on, don't be like that."

"Hmm. If I had to say, it was tough love."

At that, Jo Hyeonryang asked doubtfully.

"You hit that child? That good-natured child?"

"Would I not have been heartbroken too? But what could I do? Every
time she took the wrong path, I had to discipline her until she cried her
eyes out."

"Hmm. The rod is the best after all……"

It was a very unfortunate moment for the Jo Clan's Jo Hakche.

"But why not announce such good news? The Blood Cult Army is a real
headache, and you've dealt with them properly."

"Oh, don't even get me started. My disciple is so soft-hearted. She's
worried that the Ronin will be looked down upon just for taking the
Submerging Venom Pill. How is she supposed to survive the harsh
martial world when she's so soft? It's a huge concern, I tell you."

Ximen Surin said with a big, bright smile.

"How could her heart be so pure? Tsk."

"Even if her heart is pure, how is that a compliment for a martial
artist?"

Ximen Surin's bright smile was the brightest Jo Hyeonryang had ever
seen.

Jo Hyeonryang let out a deep sigh, his eyes full of envy.

"Well. If that is what that child wants, then so be it."

Jo Hyeonryang decided to just bury Qing's wishes. It was a shame to
abandon the honor of eradicating the Blood Cult just to take care of
some Ronin, but it could also be considered an act of chivalry.

However, the world did not always work out that way.

The problem was those Demonic Cult bastards.

\begin{quote}
{\itshape
「From the Demonic Alliance of Zhongyuan.

There are too many parasites that eat away at the world.

A prime example would be those called the Black Spots.

Look at the heinous acts of those Black Spot bastards.

They freely deal with stolen goods, so if you steal something and sell it
to the Black Spots, that's the end of it. Therefore, thieves are rampant
throughout Zhongyuan.

What about the Black Markets?

They openly engage in human trafficking, which is prohibited by
national law, daring to steal and easily sell precious human lives.

The cursed cannibals are also a problem.

These cannibals, who should be burned to death, can easily obtain
human flesh, so they hide their evil nature behind the faces of gentlemen
in their daily lives.

Moreover, they recklessly sell deadly poisons, making poisoning a
common occurrence in Zhongyuan, and they sell twisted and
unsound martial arts manuals, causing promising talents to be lost to
Qi Deviation.

They are truly harmful without a single benefit, existing only to inflict
harm on the world, malicious and vile parasites.

The new Heavenly Demon Supreme has commanded us to make the
world a better place, a world where good people are rewarded.

Thus, the Demonic Alliance, in order to eliminate the parasites that
eat away at the world, shall follow this august command.

Chivalrous ones of Jianghu!

If you, too, harbor righteousness, set aside past grudges and stand
together against our common enemy, the evil parasites, as comrades.

On behalf of the great Heavenly Demon Supreme.

The High Priest of the Divine Cult sends this to the martial artists of
Jianghu.」

「Inquiries about joining the Demonic Alliance are always welcome at
the Alliance Headquarters in Lanzhou, Gansu Province. Even if you do
not believe in the Divine Cult, even if you don't harbor the Heavenly Demon within,
we enthusiastically welcome chivalrous individuals who wish
to walk the right path 道. We greatly appreciate your interest and
support.」
}
\end{quote}

"Didn't I tell you to get rid of those Black Spot bastards! What is this
disgrace?"

Ximen Surin complained.

The proposal to eradicate the Black Spots, which Ximen Surin had
presented to the congress, was rejected by the most fair method in
human history: majority rule.

And this was the result.

"What a disgrace to the world that the Demonic Cult has stepped
forward to do a task that the Wulin Alliance had turned a blind eye
to."

"Ahem."

Originally, what was the purpose of the martial arts tournament?

Was it not to reaffirm the solidarity of the Orthodox Faction due to the
emergence of a new force, the Demonic Cult?

But now, the Demonic Cult had thrown down the gauntlet with a
morally perfect justification, completely ruining the face of the
Orthodox Faction.

"And now, there are even talks about whether the Demonic Cult has
really become good, and that the new Heavenly Demon must be truly
benevolent. What are we going to do about this?"

"Cough."

Everyone was at a loss for words, even if they had a hundred mouths.

A thousand, and they might have something to say. Like, how could we
have known that those Demonic Cult bastards would do this?

The situation had become truly complicated. Ignoring this would mean
that the Orthodox Faction was not participating in a righteous cause.

But even if they joined the eradication, they would only end up as
helpers.

It was a victory for the Demonic Brain, Ji Seungju.

Through this, the Demonic Alliance had succeeded in widely
promoting its name through chivalry and had also greatly profited from
a new business called the White Spots.

Moreover, they had used the elimination of a manageable enemy to
resolve the widespread discontent within, making it a truly masterful
move.

The leaders of the Wulin Alliance, who had dreamed of unity through
the martial arts tournament but were instead ambushed and utterly
defeated, were in a state of deep sorrow.

At that moment, Chief Strategist Sama Jong offered a solution.

"Godmother. I apologize to your disciple, but we must widely publicize
the achievements of the Blood Cult eradication. Would that be
acceptable?"

"What?"

"What? The Blood Cult eradication?"

"Why are those cursed bastards suddenly mentioned now?"

At that, the uninformed Masters began to murmur among themselves.
Sama Jong sent a look asking for permission to Ximen Surin, who
eventually nodded reluctantly.

Thus, Sama Jong explained Qing's chivalrous act.

"Oh, oh. That is truly a blessing for the Orthodox Faction."

"You see. The moment I saw her, I knew at a glance that this child was
truly a chivalrous one. Moonlight Divine Sword! How well named she
is."

The Sect Leader of Mount Hua, who was in high spirits, raised his voice,
and the Great Monk Wunue nodded in agreement beside him.

Ximen Surin's lips subtly curled upwards.

"Since things have come to this, the Wulin Alliance must also
participate in the eradication of the Black Spots. However, we cannot
be outdone by those Demonic Cult bastards, so we will use the news of
the Blood Cult eradication to show that the righteousness of the
Orthodox Faction is alive and well."

In the end, it was a matter of honor.

The Blood Cult was far more evil than the Black Spots. In fact,
comparing the two would be an insult to the Black Spots. Proclaiming
this achievement would restore the face of the Orthodox Faction.

At that, Ximen Surin shook her head.

"That won't do. If you announce that, the Blood Cult will not stand idly
by. Are you trying to make my disciple bear all that resentment?"

"So, I apologize, but could we consider it a covert operation by the
Wulin Alliance?"

"Ahem."

Ximen Surin coughed uncomfortably.

The difference between the rumor that Qing had destroyed some of
the Blood Cult and the official statement that Qing had done it was
clear.

In the former case, it wouldn't matter much, but in the latter, the Blood
Cult would have to eliminate Qing to save face.

However, they couldn't just let the face of the Orthodox Faction be
tarnished like this.

So what could be done?

"There is nothing that can be done about it. Do as you must. But since
my disciple's wishes are such, exclude any mention of the Ronin and
the Submerging Venom Pill. If you do that, my disciple will have no
objections."

"Thank you for your decision."

Ximen Surin snorted.

"Don't just thank me with words. My disciple will be the one feeling
wronged for having her achievements taken, so make sure to
compensate her well." 