\chapter{The Appearance of the Divine Dragon (14)}

Why would I wield a sword, you ask?

Qing asked back.

"Well, shouldn't you not do that if it's to survive?"

"If your skills were lacking, then I would understand, but you are already
a disciple who can be considered a Master. Now that you have the skills
to live if you truly wish to, the sword, used for survival, inevitably loses
its sharpness and becomes dull, does it not?"

"Ah."

In truth, that made sense.

If one were to reach the Late-Stage Peak Realm, they would be able to
live a life of respect if they went to any local martial arts hall.

Of course, Masters kept popping up everywhere.

But recently, had she ever really worried about survival?

Even when dealing with those Blood Cult bastards, it was the same.

She relied on her Constitution that was immune to poison.

And what did she think while doing so?

If push comes to shove, I can just run away.

Her footwork was top-notch, to the point where it could be argued to
be the best under Heaven, so she was full of confidence when it came
to running away.

From the start, she had never really worried about herself.

She worried about the Ronin and the somewhat annoying Moyong
Juhui, but she never thought she herself could be in danger.

So that's why? Because it's enough to get by?

"I don't know."

So, Ximen Surin stroked Qing's hair and replied.

"The sword held in your heart can always change. It is not a law set in
stone that must be followed once decided. And since there is no right
answer, the answer that the disciple decides on becomes the right
answer. So, my disciple, feel free to ponder without any burden."

"Mm."

To Qing, martial arts were just a convenient tool.

Honestly, she still couldn't quite believe it, or rather, she didn't feel it
was real. Or maybe it was more accurate to say that she didn't feel its
reality.

Why, you ask? Because what the hell is Inner Qi, seriously?

A versatile resource that works anywhere in the body, accumulated by
focusing the mind and breathing in the energy of the universe.

There were no such superhuman abilities in Qing's hometown.

If there were, a systemized education and management would have
designated it as a basic subject in school, thus achieving the martial
artification of the entire population and creating a billion Absolute
Masters. So… so what should be done with that?

They would all be powerless before thermal weapons anyway.

If a billion Masters mastered the Sun-Scorching Palm, they could boil
water to turn turbines.

That's environmentally friendly, right?

Or maybe a billion Masters could master Ice Arts to stop global
warming.

That's also environmentally friendly.

So, if Inner Qi existed in that modern world over there, perhaps the
Earth wouldn't be so sick?

Isn't the conclusion a bit strange……

Qing's serious 고민 turned into a foolish delusion, as it always did.

It was as if there were question marks floating all around, a sign that
Qing was making 'that expression'. Ximen Surin sighed deeply.

"Haaa. It's no use. Why can't you focus?"

However, it was more accurate to say that she was unconsciously
avoiding it rather than being unable to focus.

Instinctively, she was blocking thoughts that could lead to doubts
about the world.

So, she pushed potentially dangerous ideas to the back of her mind,
dragging the boat to a high mountain and then into the vast cluster of
stars in the universe.

"Mmm. I don't know."

Qing's shoulders slumped.

Ximen Surin stroked Qing's hair again, this time with more force.

"Originally, it is more difficult to find the truth within oneself than
objects from afar. Mm. So, instead, no. That will not do."

"Ah. Master. If you stop speaking mid-sentence like that, your disciple
won't be able to sleep out of curiosity."

To that, Ximen Surin snorted.

"Then don't sleep and train instead. That's even better."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The reason why Moyong Juhui was lying on the training grounds of the
Heavenly Martial Hall with her head between her legs was, in fact, very
simple.

She was just trying to sleep.

As a woman, she couldn't just lie down in the middle of an open outdoor
space in broad daylight.

So she took a posture that was good for sleeping.

The reason why she tried to sleep like that was also very simple.

She couldn't sleep at night.

When she was alone in the dark, she couldn't sleep due to anxiety. She
would instead crawl under the bed, hide her body, cover her mouth, and
focus on concealing herself.

Only when the endlessly long night passed, the day dawned, and the
sounds of people around her could be heard, did she feel at ease.

There was a particular voice that gave her the most comfort.

It's okay. Lady Moyong is not at fault. It will get better. It's just that
you're in a lot of pain right now, so I believe you will get better.

Those were the kind words that whispered in her ear.

When she heard that voice, it really felt like it would be so. As if that
was the truth.

That was why she came outside and tried to sleep.

But now, even that routine was over.

That bad bitch. She said she wouldn't abandon me………

However, Moyong Juhui agreed with Qing's words. After all, when she
saw Qing, painful memories became vivid.

Unknowingly, resentment and frustration that had nowhere to go
would burst out.

Yes. It's only right that I was abandoned.

Who would want someone like me?

Still, she could endure it. She had to endure it.

Because she had a home to return to. For the sake of her family as well.

What should I do? Should I tell my family?

Honestly, she wanted to just confess everything and be comforted in
the warm embrace of her family.

But that, too, was frightening and shameful.

The fact that the legitimate daughter of the Five Great Clans had been
kidnapped by the Blood Cult was a great disgrace to the family.

Moreover, she had foolishly abandoned her escort and run away alone at
night, only to be captured.

Above all, she didn't want to worry everyone in the clan because of her
own pain.

Like when Mother was sick, just like that.

Just pretend it never happened. Time will heal everything.

Just like she said, it's okay, it will be okay.

The guest rooms assigned to the Moyong Clan were as they always
were.

"Ah, Young Miss. Have you returned?"

"Yes. Uh. Where is Father? And Junie?"

"The Family Head is inside and the Young Master went out to play. He
just can't sit still, can he?"

"Well……"

Moyong Juhui trailed off.

She didn't expect a grand welcome, but her heart ached at their
indifferent attitudes.

I was in so much pain. While I was suffering, everyone just didn't
know anything, just… like that…

Moyong Seongik was the same.

"What, daughter? You're back? You said you were going home. Why did
you come back?"

"That's."

Moyong Juhui couldn't continue.

Her throat felt hot, as if tears would burst out at any moment.

This won't do. I can't be like this.

I have to talk. Otherwise, I won't be able to endure it. It's too painful to
pretend nothing happened. I want to be comforted.

Moyong Juhui gathered her courage.

But."But when you go somewhere, don't leave your escort behind. The
scoundrels of the Blood Cult are starting to stir. I know you're skilled,
daughter, but you still have to be careful."

Moyong Juhui's chest dropped.

"Blood Cult, what do you mean by the Blood Cult……?"

"You must keep this to yourself. It turns out the Blood Cult bastards had
properly set up their base in Kaifeng. Even within the Wulin Alliance,
three spies were found to be poisoned by Solitary Poison."

Among the Wulin Alliance's warriors, there were two, and one whose
family had suffered greatly. Five families of the Kaifeng government
were mourning, and even in the military, a Commander had lost his life,
so there was a series of funerals.

This was because the owner of the Blood Fiend had died, causing all
the offspring he had planted to self-destruct at once.

"It's fortunate that it was stopped early, but what a disaster that could
have been. My goodness, a military commander was a spy for the Blood
Cult. That means thirty thousand troops could have fallen into the
hands of the Blood Cult. Well, the Wulin Alliance is not in a position to
talk either, since even a High Secretary was in that state."

Moyong Juhui's eyes trembled.

She said not to tell anyone.

She said she would keep it a secret."H-How, who, who told you that?"

"Apparently, the Deputy Military Advisor found out by herself? Well.
There's no way that could be true. The General must have given her all
the credit."

Moyong Juhui was relieved for now.

It seemed that Qing had not deceived her or abandoned her altogether.

It seemed that the promise to keep it a secret had not been broken.

Deputy Military Advisor, so it was that bitch, Hyunhwa?

So, what about my story?

Did everyone find out that I was also captured?

"Don't go around telling this to others. Who knows who will be pointing
their fingers at whom. Ha. I'm so embarrassed, truly."

Judging from Moyong Seongik's attitude, it seemed that her situation
had not been revealed.

Then, maybe it would be better this way.

This time, I can just naturally say that I was also captured-

But Moyong Seongik's lament blocked Moyong Juhui's mouth.

"Anyway, the Wulin Alliance is a mess right now. Tsk tsk. There were
three spies, and you remember the other time, right? The Un Clan's
kid was said to be intelligent, so they gave him the position of
Independent Patrol, only to hand over such an important position to a
Blood Cult lackey. They made such a fuss about re-examining personnel
qualifications, but then another spy showed up."

"I-It's a bit different from that, isn't it? Once the Blood Fiend enters,
your life is at stake. Those people couldn't help it, either."

"So they sold out their comrades to save themselves. They should have
just died."

Moyong Juhui's breath caught in her throat.

Her insides twisted and turned, feeling as though they were being
shredded and convulsing in pain.

"The Wulin Alliance is in an uproar right now. They say all departments
are in chaos trying to figure out how far the information was leaked."

"That's."

"Honestly, what do you expect from those who know what happened to
the Jinju Un Clan? Didn't a spy from the Blood Cult annihilate a clan that
had entered the Ten Great Clans? And it wasn't just the annihilation. It's
said that they turned all those numerous family members into jiangshis,
which is even worse than death."

Moyong Juhui's face drained of blood.

Luckily, she was sitting down. Otherwise, her legs would have given out
and she would have collapsed.

However, her mood had already fallen to rock bottom.

"Daughter? Why do you look like that?"

"I-It's, still. Those people didn't know they would be captured by the
Blood Cult, that's not their fault. They probably didn't even think they
would be captured."

"Shouldn't a martial artist have died resisting rather than being
captured? If a martial artist is captured alive, that alone is already
utterly shameful. And if they knew they were poisoned by the Blood
Fiend, they should have either killed a few bastards and gone down
together or informed the Alliance. They must have begged for their
lives, saying they would do anything to survive. Ha. What pieces of
trash."

"Ugh."

"Daughter?"

Vomit. Vomit. Vomit. In the end, unable to withstand the turmoil inside
her, Moyong Juhui vomited out the contents of her stomach.

"Wh-What's wrong? Are you sick? A physician, a physician, yes, the
Tang Clan, someone, no, wait a bit, daughter, I'll call someone right
awa-"

"No! No, it's nothing."

Moyong Juhui screamed in a voice close to a shriek.

The Tang Clan could not know. The Tang Clan must never know…….

"I was just a bit queasy, so I ate something to settle it. It's, it's better
now."

"Aigo. You tried to settle your stomach by eating? How foolish."

"Hehe, hehehe……"

Moyong Juhui forced a smile.

At that, Moyong Seongik, unable to shake off his worried expression,
gave a stern warning.

"Don't hide it if you're sick. If I see your mother's state again, this
father will truly go to the afterlife then. Do you understand? Daughter?"

"Of course, of course."

Moyong Juhui tried to smile, desperately, and with all her might.
She just swallowed her screams inwardly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Since the martial arts tournament and all the major events were
coming to an end one by one, the finals of the Hidden Dragon Sparring
Tournament was the biggest event to mark the grand finale.

It was said that many unexpected events occurred during this Hidden
Dragon Sparring Tournament.

However, people's minds change like the weather, so now it seemed
like they had completely forgotten the past and were saying
something else.

Qing had defeated Wolbong in a clearly convincing and spectacular
match, during which she had also revealed her beauty. Moreover, it was
later revealed that she was the disciple of the Zenith Among Women.

And after that, those who had been talking about the Ugly Swordswoman
and how an ugly woman had to be skilled in martial arts at the very
least, all nodded with solemn expressions.

- I knew it. There was a certain unique grace about her from the very
beginning. And with such prowess at her age! Indeed, she is just as
expected of the disciple of the Zenith Among Women.

- Ha. Look at these fuckers talking shit after betting on the wrong horse.

- What? What the fuck is this son of a bitch saying……?

For some unknown reason, after the semi-final match, various fights,
both physical and verbal, had become unusually frequent in Kaifeng.

In every restaurant, pub, eatery, and teahouse in Kaifeng, people were
raising their voices and arguing, their faces red with anger.

Usually, when such a trend arises, it is a phenomenon that occurs when
a topic of obvious interest to everyone circulates, and everyone rushes
to express their opinion.

Thus, the topic that had people raising their voices wherever they
gathered was this.

What kind of title would suit the disciple of the Zenith Among Women,
Ximen Qing of the Divine Maiden Sect?