\chapter{The Appearance of the Divine Dragon (5)}

-Waaaaaaaaah!

-Woooooooah!

The shouts that shook the martial arts arena poured down.

Of course, since Qing's betting odds were extremely low, countless
dreams were shattered and fell into the abyss. However, the content of
the duel was so spectacular that the financial losses were overshadowed.

After all, wasn't it a legendary duel where Qing's sunset-like True Qi
bloomed in all directions, and even the splendid golden Sword Force
could be witnessed with the naked eye, making it a spectacle that one
could not even take a breath while watching?

Indeed, it was a sight to behold and talk about for the rest of their lives,
giving them the pride of having witnessed a monumental event of an
era.

Yes. It was a monumental event of an era.

A single woman. Not even from the Nine Great Sects, but from a
significantly lower-ranked small sect.

To emphasize again, a female martial artist!

Together, a female martial artist from a small sect defeated the
disciple of the Great Monk, the Greatest Under the Heavens, of the
Shaolin Sect, the very best of all under Heaven!

Moreover, and even more so, that wasn't all!

The Divine Maiden Sect was a sword sect, and Ximen Qing was a
swordsman!

A swordsman who used a sword put aside her sword and fought with
fists and palms to shatter the divine arts of Shaolin, defeating the
disciple of the Greatest Under the Heavens.

Of course, the ending was a bit anticlimactic, but to the eyes of
ordinary people, it seemed as if Qing, with her spectacular evasions and
long, sweeping movements, overwhelmed the duel.

Since the perspectives of Masters were no different, it was a result
acknowledged by everyone in the world except for Wolbong.

The excited cheers did not subside even as Qing disappeared and
passed through the tunnel under the dueling platform. Well, she didn't
have any particular thoughts about the booing, but this kind of reaction
made her feel somewhat good.

"You were always great, but today, you were even greater. Are you
hurt anywhere?"

"Of course not. You know how sturdy I am, ouch."

Qing, claiming to be fine, ended with a sharp cry.

It was because Ximen Surin poked Qing's chest with her finger.

"If it hurts, say it hurts. You foolish thing, always saying you're fine."

"Hehe, actually, even though this area is weak against cutting and
stabbing, it's strong against blunt force. It might just bruise a bit, but it
acts as a shield, effectively defending against impacts to the torso-"

Thump. Ximen Surin lightly knocked her head.

"You hardly seem to care about yourself, so this teacher feels relieved.
Since anything can happen in a duel, I was just going to say not to
blame yourself even if he hit your chest or aimed for your face, as that
is only natural."

Surprisingly, Ximen Surin had no ill feelings towards Wolbong's
attacks, regardless of the area.

In fact, she was more upset when he was timidly avoiding and attacking
sensitive areas, asking how he could discriminate between men and
women as a fellow martial artist.

For this reason, Ximen Surin used to kick up between the legs when
treated like a woman. As such, her notoriety as the Female Mad Dog was
not unfounded.

Because of this, when Wolbong showed his true intentions, she thought
it was good that he was a proper man who recognized her disciple as a
martial artist.

Of course, she found out that he was just a very, very despicable guy
who didn't treat her like a woman because he thought she was an ugly,
veiled woman, but still.

"Hmm. Let's apply some makeup now. I should give you time to wash
and tidy up before the introduction. Why are they in such a hurry? Tsk
tsk. There are only men in the Wulin Alliance, so they are not
meticulous at all."

Ximen Surin clicked her tongue.

The event after the semi-final duel was a moment to introduce the
martial artists who had advanced to the finals of the Hidden Dragon
Competition to everyone.

The reason why the participants in the Hidden Dragon Competition
were only known by their origins and names was to focus on the duels
themselves.

Therefore, before the finals, a place was prepared for them to proudly
reveal themselves and elevate their names before the world.

"Uh, do I really have to put on makeup? Since it's a place to present
myself as a martial artist, wouldn't it be better to act like a martial
artist-"

"As this teacher has repeatedly said, Masters must be elegant and
beautiful. Didn't that young monk say the same thing?"

Ximen Surin was drilling the conduct of a beauty into Qing.

There were no men and women in front of martial artists.

But there was beauty and ugliness.

Even if one was a Master who had the whole world under their feet,
they would not be recognized if their appearance and conduct were
ugly. Whether they were male or female, it was the same.

If you're ugly, you should at least be skilled in martial arts. Since you
were born ugly, you had no relationships with the opposite sex and were
ashamed to go outside, so you could only focus on martial arts, right?

That was what people would mock.

Although it was said not to discriminate between men and women, in
reality, female martial artists were treated much worse.

Even an ugly man, if he became a Master, could marry a beautiful wife,
accumulate wealth and fame, and live prosperously.

However, if an ugly woman was a Master, it was common for her to live
alone for the rest of her life, as men did not want to live with a wife
who would beat them up. After all, it was no different from saying they
wanted to be beaten from the start, so such was the perception of the
world.

Ximen Surin, taking out her makeup tools, spoke.

"Now then. Shouldn't we show the world? That the next Greatest Under
the Heavens is such a beautiful woman."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Wolbong could not raise his head.

He was ashamed of his embarrassment over Qing's beauty and the
rising of his Yang Qi, so his head was dizzy, and the words that came
out were even more dizzying and embarrassing.

"I apologize. Teacher, this disciple has been foolish and has disgraced
the name of our sect and my teacher."

Then, Great Master Wunue chuckled.

"What are you talking about, you brat? The only names you disgraced
were yours and your face. Why are you selling out the innocent Shaolin
and your teacher? Hahaha, I knew this would happen, you brat."

"Teacher?"

"Did Shaolin relinquish its title as the greatest sect under heaven just
because you lost in both martial prowess and as a human being? Did
the Divine Maiden Sect suddenly become the greatest sect? Did my
realm drop because my disciple lost? I am still Wunue, the Greatest
Under the Heavens, so the only one tarnished is you, you fool. Shaolin
and your teacher are perfectly fine."

That was indeed the case.

The one who suffered shame was Wolbong, not Wunue, and Shaolin's
stature was not shaken by such things. No matter how fierce the wind
blew, a mountain remained steadfast in its place.

"You were so arrogant that I knew you would be greatly disgraced
someday. Why do we call it being foolish? Isn't it because one is
actually foolish? Since the foolish do not listen when told with words, I
kept quiet to let you experience it yourself. How does it feel?"

"It is… wretched and shameful……"

"Well. Everyone carries at least one memory they want to erase in their
hearts. Alright, go get ready to show that face of yours and greet
everyone. Tsk, your head has a very clear handprint. It seems your
teacher's hand is quite spicy……"

Indeed, the mark of the palm that Qing had struck was clearly
imprinted on Wolbong's forehead, extending to the crown of his head.

"Teacher, how can I face everyone after such a disgrace? I am afraid. I
am too afraid that people will laugh and mock me."

"Hey, it's not a big deal. You're going to live for more than fifty more
years, so do you think that one incident will tarnish a monk's life with
disgrace? After some time, it will just be a funny memory, so you should
blame your own shortcomings."

"But."

"Well. That child's beauty is quite extraordinary, so, ahem, ahem! Mara,
isn't it called Mara! It's truly a masterpiece! Mara Papiyas! As if you are
some kind of living Buddha like the Great Sakyamuni, does it make sense
for the Demon King of the Sixth Heaven to come down and tempt you
himself! Hahaha!"

Mara must descend in person to tempt someone of at least the level of
Buddha, so would he come down to tempt a mere young monk of
Shaolin?

Great Master Wunue burst into laughter.

The other high monks of Shaolin also laughed, smiled, or at least
scoffed, so Wolbong alone was at a loss for what to do.

"That's why I'm saying you're arrogant. And when a person makes a
mistake, they should be ashamed. Go and be thoroughly ashamed. A
man can make a mistake. Moreover, well, that child's beauty is not
ordinary, so people might understand your feelings, maybe, possibly,
perhaps, perhaps not."

The last long, drawn-out question was a way of saying it didn't matter
either way.

Since his teacher's attitude was like this, Wolbong's shame also
lessened its intensity like a wildfire.

"Go and change your clothes. Don't even think about covering it with a
hood. It's better to show it openly, as those who are close by will see it
clearly and spread rumors, which would be even more embarrassing."

With that, Wolbong drooped his shoulders and left to change his
clothes.

Only then did Great Master Wunue mutter with a serious expression.

"Hmm. Anyway, the Buddha's Palm, huh. What should I offer to match
the value of that divine art? If I'm not careful, I might commit the
blunder of putting a price on a priceless treasure, but……"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

As soon as the duel between Qing and Wolbong ended, people jumped
up from their seats.

They were the people who had bought seats on the floating dueling
platform to see the heroes of the Hidden Dragon Competition up close.

Since the Wulin Alliance was, of course, a group that needed money,
they were thorough in making money when they could.

As the Wulin Alliance's martial artists called out 'Armor Seat' or 'Silver
Seat', people were guided, and despite the complexity of the event,
people were gradually seated on the floating dueling platform without
much fuss.

Of course, this was not due to the excellent sense of order of the
people of Zhongyuan but because the Wulin Alliance's staff
were all armed with swords.

It was a virtue of this uncivilized era to listen well to those with swords.

Thus, starting from the very expensive Armor Seats (which were, of
course, standing seats) closest to the introduction stage, people were
gradually seated.

Those who didn't have money or didn't think it was necessary to see
them up close just watched from the arena seats.

However, they also thought that since they had come to watch, they
should have spent some money to go down to the lower level.

It was because they were so curious about the beauty of the Divine
Maiden Sect's disciple who had even captivated a Shaolin monk.

And so, finally, starting with the quickest to be eliminated, the Hidden
Dragons of the competition were introduced to everyone.

They introduced not just their origins and names, but also their age,
region of activity, history, any titles if they had them, and if they had a
sect, the history of the sect, and if they had a teacher, their teacher's
name as well.

As a result, the introductions of those from rogue backgrounds tended
to be a bit lacking, but it was also true that rogues didn't have much to
boast about in the first place.

Wang Nopil and Ma Yeongjeon had made it to the final eight, so they
came up much later.

In the place where the four losers of the final eight stood side by side,
Wang Nopil and Ma Yeongjeon exchanged glances and shook their
heads.

Originally, they had planned to slightly fabricate the story related to
the Blood Cult and tell it to everyone in this place.

Saying that Young Lady Ximen had been captured instead of them could
create rumors that were unfavorable to her, even if it was only for a
day, so they decided to exclude such disadvantageous details and
elevate her name with a tale of the courage of foolish rogues and the
martial prowess that defeated the evil Blood Cult.

After coordinating the story, they asked for Ximen Surin's permission,
wondering if such an announcement would harm Young Lady Ximen in
any way.

However, they were told not to do anything unnecessary and received a
nuclear head-butt each, so they just dropped the matter altogether.

Then, it was the turn of the semifinal losers, Wolbong, and, coincidentally,
the one who appeared with him was the Most Handsome Man Under
the Heavens, Jade Qilin.

Sharp screams shook the heavens and earth, and many grimaced at the
pain in their eardrums. Of course, many women also fainted.

-Jade Qilin! I love you!

-Jade Qilin! You're so handsome!

-Jade Qilin! Take all of my body and soul!

The content was one of pure love, but the screaming of the shrieking
voices made even Wolbong, who was standing next to them, feel
chills.

It felt like an obsession beyond love, even bordering on ghostly
possession, making Wolbong glance at Peng to see if he was okay.

It seemed like he wasn't, as he was grinding his teeth and frowning
deeply.

After Peng Daesan, who had fought first, was introduced, it was
Wolbong's turn.

Twenty-seven years old this year.

The youngest Arhat of the Shaolin Temple.

A young Master of Shaolin who had the Greatest Under the Heavens,
Great Master Wunue, as his teacher!

At the host's shout, a cheer of 'Waaaaaah!' swept through the arena.
Wolbong's shoulders, which had been hunched, straightened a bit.

-Hehe, to think they would use hand seals instead of the prayer beads!

-I forfeit! If I use up all my Inner Qi, I'll have to forfeit!

-Hehe! Now I will do my best!

Of course, there were those who scoffed, but Wolbong, who had been
terrified of standing alone amidst the great humiliation with only
jeers, found it bearable.

And then, it was finally time for the finalists to appear.