\chapter{The Appearance of the Divine Dragon (15)}

The New Dragon referred to one who had completed the long life of an
Imugi1 and newly ascended to become a dragon.

It was also a respectful title given to the shining star who won the
Hidden Dragon Tournament.

The problem was that for a very long time, no woman had ever won.

And so, naturally, the debate began here.

Originally, the term 'dragon' referred to a man and 'phoenix' to a
woman. That's why the Rising Stars of the Orthodox Sect were called
dragons and phoenixes.

Therefore, wouldn't the title that should be given to a disciple of the
Divine Maiden Sect be New Phoenix, not New Dragon?

Then, someone else would intervene.

Or, if they were close enough, they would dramatically agree at the
same table, 'Well then, New Phoenix it is, indeed.', only for someone at
the next table to intervene upon overhearing.

Even so, New Phoenix sounded a bit lame, didn't it? There was no
record in Jianghu's history of such a tacky title for a Rising Star.

Then, opinions would be divided once again.

The female form corresponding to the New Dragon should indeed be a
young phoenix, Bongchu.

What's the difference between a man and a woman when it comes to
martial artists? Following the long tradition, it's right to call her the
New Dragon.

As such, there was no place in the city of Kaifeng where a fight wasn't
breaking out.

However, everyone agreed on one thing: the disciple of the Divine
Maiden Sect would win.

After all, she had defeated even Shaolin to get here.

It was true that the martial prowess of the Gongson Clan's woman, who
had engaged in a high-level duel with the Jade Qilin, was also
astonishing.

But Qing was a swordsman who had defeated Shaolin with just
physical strikes.

Originally, wielding a weapon was far stronger than not. This was a
basic fact that even a newborn baby knew instinctively from the
moment it left its mother's womb.

However, the fact that she had defeated Shaolin, which boasted the
greatest fists Under Heaven, with her bare ists was evidence that her
achievements with the sword must be even higher. Or so it was said.

And so, everyone was in an uproar, trying to come up with a plausible
title.

One might scoff at the idea of creating a title for someone else, but if
one could coin a splendid term that resonated with everyone, it could
become widely used as an unofficial title.

There were many martial artists who had several such unofficial titles.

If the title one created became widely used unofficially, it would be a
source of pride to pass down through generations. So it was no wonder
that the people of Zhongyuan, who were serious about their
pride, wouldn't miss this opportunity.

"I heard she's a beautiful woman. How about Seoshi Sword? Seoshi
Sword is too old-fashioned, you say? Then, how about Seoshi Divine
Sword? Do we really need to attach Seoshi to it? I think Three-Headed
New Dragon is quite good. Three-Headed New Dragon? How can a
dragon have three heads? Ah. That's right. Three heads. Then, it should
be Three-Headed Young Phoenix, not a dragon. I understand that much,
but a dragon or a phoenix with three heads sounds like a monster,
doesn't it? Since she's a new beauty, shouldn't she be part of the Six
Flowers of Wulin? Then, we should call her New Dragon Sword Flower.
But then, wouldn't there be two Sword Flowers? Then, how about New
Dragon Divine Flower? Hmm. I think you'd better just listen quietly
instead of trying to come up with a title."

However, the approaches to the title were quite infuriating for Ximen
Surin.

There was no praise for her divine presence, only talk of her being a
beauty or having large breasts. In fact, it was based on the underlying
wicked mentality that wondered what use a strong woman could be in
Jianghu.

Thus, on the day of the final match, countless cheers poured down on
Qing, who elegantly ascended and lightly landed.

The sound was even more thunderous than when the Shaolin disciple
appeared, truly shaking the heavens and earth with its maximum
volume.

Qing used her transcendent hearing to pick up a few things being said.

Hmm. What?

Three-Headed Beautiful Phoenix, ugh, who the hell came up with that?

I need to keep an eye on them.

Breast-Flaunting Divine Maiden? How fucking ridiculous.

Flowery Pig? A pig, you say?

Papae2 referred to a woman with large breasts, meaning 'dominant
waves'. It was a term Qing had heard quite often during her beggar
days.

It wasn't a compliment in Zhongyuan, where large breasts were
considered a flaw. It was similar to calling someone a pig.

In fact, not long ago, even in Qing's hometown, calling a busty woman a
'milk cow' had just started to become popular.

Across both East and West, derogatory terms for women with large
breasts involved pigs. It was a word with deep roots. And since largebreasted women were looked down upon in Zhongyuan, it
translated to something like 'pig bitch'.

But 'flowery pig' was a different story.

It was the most affectionate, or rather, the most flirtatious term the
people of Zhongyuan used to address their lovers.

Although she had large breasts, the term 'flowery pig' was filled with
the humor of Zhongyuan, suggesting an intention to cherish her.

It was a fucking ridiculous sense of humor, though.

Of course, it wasn't all just songs about breasts.

The Mountain-Uprooting, Earth-Shaking, Overturning Lady.

Lady Xiang Yu, hmm… was it common for the name Xiang Yu to be
followed by 'Lady'?

It seemed her strength, displayed when she grabbed the Shaolin
monk's wrist and slammed him down, had left a deep impression.

The Most Beautiful Woman Under Heaven was a bit much. There are so
many pretty people Under Heaven, so it's a bit embarrassing.

Sword Empress Beauty, they're already calling me a Sword Empress,
huh……

Her heart fluttered at the cheers directed entirely at her. Hmm. This
isn't so bad, is it?

But still, calm down, everyone.

Qing raised her hand to calm the crowd.

Following her, Gongson Yoyeh appeared, but the cheers were not as
loud, making it an incredibly awkward situation for her.

But it seemed she had earned a cool title, the Xuanyuan Heavenly
Maiden. What? Why does it sound so plausible?

"Young Lady Ximen. I hope you haven't forgotten my request?"

"Yeah. I don't really get it, but I'll do my best."

I've been thinking hard about it all day yesterday and today, but I still
don't really get it.

Does fighting with the intent to kill make it sincere?

"Then."

Gongson Yoyeh bowed slightly, then raised the longsword she firmly held
with both hands.

Then, a giant sword's shadow was cast. A thick sword shadow that
vertically crossed Qing's face. A massive Sword Qi that split the sky in
two soared high and spread majestically.

The immense energy within made Qing grit her teeth.

This is the true, original Heonwon Sword, which consumes Jinwon,
huh.

In response, the Sword Qi from Qing's sword also flared to its
maximum output. The Sword Threads grew so large that they almost
resembled a greatsword, a specialty of Qing's called the Sword Qi
Transcendence.

The long, one-jang3 high sword of Gongson Yoyeh and the broad Sword
Qi greatsword of Qing clashed loudly with a BANG.

An intense pressure, unfelt in the simple Mountain-Pressing
Downward, pushed in.

The familiar, throbbing Sword Qi.

The mighty force fueled by burning one's life.

Ha. Me too, seriously. I'm so fucked.

I was underestimating Gongson Yoyeh, thinking I would win anyway,
and now I'm pushed back by just one move.

But isn't that completely cheating?

What kind of sword extends like that? And if you're swinging a onejang long sword, how wide would the range of that attack be?

A long sword also means a long reach.

And since it swings in a radius from the center, the speed at the end is
like a ray of light, drawing a surface rather than a line as it rushes in.
I wonder if this is how martial artists feel when facing a swordsman.

How do I narrow the distance?

As if to demonstrate that this was just a taste, a horizontal slash that
occupied the space followed.

The weightless Sword Qi could be blocked but not deflected, only
applying pressure by pushing it gently.

Gongson Yoyeh's Sword Qi was a noble color, dyed in a precious dye
between red and purple, the color of an emperor.

Qing pushed back the straightly extended Sword Qi to the right and
took a step. With a scraping sound of Sword Qi clashing, sparks of
Sword Qi scattered in all directions, following the blade and
connecting to Gongson Yoyeh in a straight line.

Then, suddenly, the pressure on the sword was released. It was
because Gongson Yoyeh's sword had shrunk, shortening the Sword Qi,
causing their clash to break.

Qing's sword, which had been pushing with force, swerved through the
empty air. Her body staggered as she leaned forward.

Gongson Yoyeh's sword turned from a line into a point.

It was a thrust aimed directly at Qing.

It was hard to say whether it was a thrust of a Sword Qi that simply
extended, though.

Qing freaked out.

Iron Plank Bridge? No. I can still bend downwards.

The sword was still far away, so Gongson Yoyeh's sword was very
flexible. Even after thrusting, just lowering it would make it a fatal
blow, vertically splitting the Iron Plank Bridge.

Qing threw her body into a posture of diving into the water.

She rolled twice on the floor and stood up, only for the extended Sword
Qi to chase after her.

Powerful Jin Qi surged from Qing's Yongcheon acupoint. The
Yongcheon acupoint was located on the sole of the foot, between the
two bones of the forefoot.

Thump, thump, thump. Qing's strides lengthened, drawing a large circle.

Her gaze was fixed on Gongson Yoyeh.

Qing spun, gradually narrowing the distance towards Gongson Yoyeh at
the center.

Chasing after Qing's back, Gongson Yoyeh's Sword Qi disappeared.

It was as if she was telling her to stop spinning and come closer, lightly
placing the tip of her sword on the ground and standing as if using it as
a cane.

Qing responded to that call.

The Gyeokgong Attack, the unparalleled Swiftfoot Art that was almost
all of Swiftfoot, was deployed. In an instant, Gongson Yoyeh's entire
body expanded to fill only the upper body in Qing's vision.

Just as Qing was about to unfold the Divine Maiden Sword's form-

Suddenly, a strange flow of the atmosphere was felt on her face and on
the skin of her hands. Qing stomped on the sparring stage with her
heel! The floor shattered, and pieces of wood flew up from the
ignorant stomp. Qing's body shot straight back.

And high up in the sky, she saw a loose net surrounding Gongson
Yoyeh. The trajectories drawn by the Sword Qi covered all directions,
unfolding in the shape of a net.

Wow. Awakening Divine Arts. This is working out quite well.

But what the hell is that?

When martial arts reached a certain level, they touched upon
ideology. It was a miracle of drawing out a sword of the heart, defined
by the individual, beyond just swinging a blade fast, slow, strong, or
soft.

Gongson Yoyeh's move was something Qing didn't know the name of,
but if she had to name it, it would be something like Instantaneous
Killer Slash.

However, each of those slashes contained the profound mystery of
encircling all directions, drawn by speed from an immense force that
had reached its peak.

Spreading out in all directions like a blooming rose, the net of Sword Qi
suddenly disappeared as if it had never existed.

Gongson Yoyeh smiled and spoke.

"Young Lady Ximen. You won't be able to push through like you did
with Monk Wolbong. That… honestly, it wasn't really martial arts, was
it? You were just overpowering him with your innate strength and
senses. Please, don't do that. I'd like to see your true sincerity."

"I don't really get what this 'sincerity' thing is. All the martial arts I've
learned are for killing. If I use my Killing Sword, does that make me
sincere?"

"Well. I wouldn't know that. Young Lady Ximen must have her own
martial arts."

"My own martial arts, huh."

A sword is a tool for cutting.

In the first place, wasn't that the same for all of human history? Or was
it a tool for rituals? Or a symbol of power?

Is there really a depth that can be called a scholarly pursuit?

"Alright. It's my turn now."

Thump! The sound of her steps was sharp.

Gongson Yoyeh's speed was extraordinary.

It was different from the speed seen in sparring, so it must be the
power from burning her Innate Jin Qi.

If I drag this on, she'll keep consuming her precious Jinwon. It would
be better to end this quickly, even if I have to use my Killing Sword.
Qing's stance changed.

She immediately moved her left hand softly, and a solemn sound of a
Buddhist bell echoed. However, the result was devastating. A giant
handprint of Buddha was stamped into the sturdy wooden floor of the
sparring stage.

At that moment, the Shaolin monks in the audience stood up and
chanted the Buddha's Palm in unison.

But as if she had expected this, Gongson Yoyeh had already ducked
under Qing.

This bitch, she can go even faster?!

Qing's sword tip extended towards Gongson Yoyeh's nape. Then, a
hand that pushed away the blade. Gongson Yoyeh's left hand was also
not idle.

Qing twisted her sword. As if to cut the hand daring to touch her sword.

But an auspicious colored Inner Qi flared, and with a small explosive
sound, Pang, Qing's sword flew far away.

Gongson Yoyeh raised her sword, pointing the hilt towards Qing's
temple like a hammer.

In an instant, Qing's eyes flashed.

Kwaaaareung! Along with the sound of thunder, the sunset-colored
Jin Qi of the Zhu Yang's Heart Cleanse Mirror erupted. Ppak! With a
sound of striking bone, Gongson Yoyeh's shoulder was roughly pushed
back.

It was the defensive lightning of the Self-Protection of the Purple
Lightning Demonic Art, one of the Ten Great Demonic Arts Under
Heaven.

Hmm. I thought it would work. And it really did.

It was thanks to her senses, sharpened to their peak by the effects of
Awakening Divine Arts. Her perception of the atmospheric flow was
much sharper than usual, so she judged that she could control the
Purple Lightning Demonic Art as well.

Even if she couldn't control it, it would have just hit somewhere else,
but the fact that it hit the shoulder she aimed for made her happy.

But should I really be using this?

Eh. Whatever. Sincerity is what matters, right?

Teacher said to just bullshit my way through it if I had to.

It's not purple, but a sunset color, so if I say it's the Zhu Yang Demonic
Art, no, since it's a Demonic Art, it can't be that. Then, how about the
Zhu Yang Divine Lightning Art?

Qing smiled wickedly. 