\chapter{The Appearance of the Divine Dragon (8)}

There are many ways to accumulate merit in Buddhism. Among them,
the easiest is the act of reciting sutras, reading scriptures.

According to the teachings of Mahayana Buddhism, the merit of
sharing any sutra by filling the space with its sound is immeasurable,
meaning infinitely virtuous.

Furthermore, sutras are also called the Luminous Light of Wisdom,
which means they are a great lighthouse that guides one to
enlightenment (wisdom).

Therefore, reciting sutras aloud is an act of finding direction by looking
at the only light that shines in the dark world where one cannot see an
inch ahead due to all kinds of delusions.

Therefore, if one recites a sutra knowing its meaning and with genuine
intent, there is no greater merit than that.

But even if one does not know its meaning, is there anyone who does
not recognize the brightness when looking at the sun?

Therefore, simply reciting a sutra properly according to its text
naturally accumulates merit that leads to Nirvana.

In other words, it is an easy and free method of practice!

Wunue did not intend to impart martial arts to Qing.

Since he already had a disciple, he did not covet after brilliance nor scorn fate, even though Wolbong fell short when compared to Qing.

Moreover, it would be excessive to give her something she did not
particularly need.

So, he only wanted to lend a hand in suppressing the Heavenly
Slaughter dwelling in her mind by having her memorize a bright verse.

Thus, a very peculiar language came out of the Great Master Wunue's
mouth. It was an indecipherable language where a slight difference in
pronunciation, made by exhaling breath, could completely change the
meaning of a word.

This was Sanskrit, the language of the land where Buddhism originated.

However, Wunue was unaware that Qing had a built-in universal
translator.

As soon as she heard the sutra, the Martial Arts Window sparkled and
registered a new martial art in the standby state.

And it even had a purple border.

\textit{The Dragon-Elephant Prajna Heart Sutra?}

\textit{Hmm. It's purple, so it must be good, right?}

"Now. That's it for one recitation. It is a bit long, but if you slowly recite
it in your mind while circulating your Qi, you will surely experience
good things. Now, I will recite it again. O'Hum-"

"Uh, Great Master? Do you perhaps keep repeating it until we memorize
it all?"

"Of course. Reciting sutras is in itself a form of merit. This is a wisdom I
received directly from a high priest of Tianzhu, so just reciting it
during your Qi circulation will imbue you with the profound spirituality
of Buddhism. And as I said, you should memorize it while your mind is
still young and malleable."

Originally, Sanskrit was quite lengthy.

To be precise, the Chinese characters used in Zhongyuan were
incredibly short. This was because Chinese characters were the most
primitive and foolish method in the entire universe, across the past,
future, and all of the three thousand worlds, of memorizing pictures.

One of its advantages was that it was short.

However, since it was short, one had to attach annotations to the text,
and since the annotations were also short, one had to attach
annotations to the annotations, thus doubling or tripling the work.

If she tried to memorize it the normal way, just by listening to it all day
today, she still wouldn't be able to.

Qing bowed her head, closed her eyes tightly, clenched her teeth, and
raised the level of the registered martial art in her Martial Arts Window
to one.

When she was alone, she would just let go and make a fool of herself by
rolling her eyes back, trembling, and drooling as her brain was
ruthlessly violated. But she couldn't show such a disgraceful sight in
front of a monk, so this was her plan to not make it too obvious.

Since he told her to memorize it right away, she had no choice but to
level it up to one and implant it in her brain.

"Hmm? What's wrong?"

"I, thi, thik, I've memorised it."

Due to the lingering effects of having her brain messed with, her
pronunciation was off.

"What? You memorized it after hearing it twice? Is that even possible?
Even I had to meditate for half a day and was beaten with a bamboo
stick before I could barely memorize it."

"I, I'll recite it once, so please tell me if there are any mistakes."

Thus, Qing recited the sutra she had memorized through a shortcut.

When Sanskrit flowed out from a woman's beautiful voice, it truly gave
off a strange and mysterious feeling.

Anyway. She really had memorized it all!

"There's no way this is possible. Again, try it again."

"Yes. So……"

"Again."

"Again."

"Again."

It was only after reciting it ten times that Wunue muttered in
disbelief.

"If you had focused on studying rather than martial arts, the world's
greatest sage would have been born. Alas, you were born in a woman's
body, so the will of heaven could not be fulfilled."

If Ximen Surin had heard this, she would have launched a carpet
bombing of nuclear head-pats.

However, it wasn't exactly wrong because the primitive Zhongyuan
did not recognize women's studies.

To begin with, the governing principle of Zhongyuan was
'Gonggwijwasang Joegwibwain', which meant that all merits belonged to
the Emperor and all sins belonged to women.

This was why when a country fell, it was blamed on women's sins,
calling them women who ruined nations, such as Daji and Yang Guifei.

"Yes. You have memorized it all. Recite it ten times when you wake up
in the morning, recite it in your mind whenever you circulate your Qi,
and recite it ten times before going to sleep. Then, you will surely
experience good things. Especially for you, who carries the ominous
starlight of the Heavenly Slaughtering Star, it is a very precious
teaching, so do not take my words lightly. Do you understand?"

"Yes, I understand, eh, you knew?"

Qing asked in surprise.

How could he just suddenly bring that up like that?

To which, Wunue snorted.

"A Great Master can tell just by looking. It will be of great help in
suppressing the Heavenly Slaughter, so do not take my words lightly
and recite it morning, noon, and night. Do you understand?"

"Yes. Thank you."

"Yes, you should be thankful."

"Oing?"

Usually, shouldn't it be 'Please be thankful' here?

Then, the Great Master Wunue laughed heartily and said again.

"Gratitude is the feeling of being moved by grace. I, too, was moved by
your willingness to return the Divine Arts, so would I not have
gratitude? We have given and received virtue to each other, so it is not
something that never happened. Rather, by being grateful to each
other, we increase our merits, and this is what is called dependent
origination."

Qing made a face as she looked at Wunue.

What is he saying? Why is dependent origination suddenly coming
up? Does he want me to act out my gratitude?

To which, Wunue burst into laughter again and stood up from his seat.

"Kuhaha. Alright. If the Secret Manual is completed, bring it to
Myeongbeopsa Temple. Should an old monk have to come all the way
to get it? You should get some exercise while you're young."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

At night, Cheon Yuhak held out a pair of shoes to her.

"Here. These are shoes for your training. From now on, wear them."

"Ehh. What kind of shoes are these?"

It was questionable whether the object Cheon Yuhak presented could
be defined as shoes.

The sole only covered the front part of the foot, and behind it was just
silk that wrapped around the back of the foot and drooped down.

Moreover, the arch of the foot and the heel were completely exposed,
so if she stood upright, they would directly touch the ground.

"If I wear these, I'll have to walk on the balls of my feet."

"That is why they were made."

"If I don't lift my heels, this fluttering part will drag on the ground and
get dirty."

"You have to lift your heels so it doesn't drag."

"And what are these bells for? Am I a child that needs to make noise to
announce my presence?"

Qing shook the shoes.

Luckily, since the clappers were heavy, it didn't make a loud,
obnoxious, jingling sound. But it still made a sound like shaking a
money pouch.

"So, when you take a step, only use the balls of your feet. Ah, the sole is
also layered, so if you step too hard, you'll make a clapping sound. So
take each step gently so that neither the sole nor the bells make a
sound, and move with fluidity."

If she got used to this, her footsteps would make no sound at all.

It was the secret to how Cheon Yuhak's footsteps were completely
silent.

"Can't I just walk around comfortably……"

"Think of it differently. Just by wearing those and walking around
without making a sound, you'll be training. Isn't it practically free
training?"

"Oing?"

Qing's eyes widened at the unexpected change in perspective.

Come to think of it, uh? That's true?

"That's level one. Once you get used to it, you'll change to soles that
make more noise and lighter bells. If you can walk around without
making any noise even at level three, then you'll be able to walk on
fallen leaves without making a sound."

"Oooh."

At that, Qing was completely won over.

And the result of that was…

"Agh, shiiiiit………"

Where in the world can you find free training?

Training was originally arduous and difficult.

The fact that just walking around was training meant that just walking
around was arduous and difficult.

The front sole of the shoe was made like the clappers of tap dancing
shoes, so even a light step made a loud 'clap!' sound.

The sound of silver coins clinking came from the bells hidden inside the
silk draped over the heel.

So with each step, clap, clink.

And with another step, clap, clink.

Moreover, since there was no sole on the heel, she had to walk on the
balls of her feet the entire time. To prevent the draped silk from
dragging on the ground, she had to lift it up much higher than she
thought, practically tiptoeing around.

Still, Cheon Yuhak's words were somewhat of a consolation.

"Wow. They say even a worm can turn over if pushed. To think you
would be so proficient from the start. You'll get to level two in no
time."

Since Qing's body was far from ordinary, her heels didn't hurt or tire
from being lifted. It was just uncomfortable; as such, she could walk
around very well.

Then, Whack!

The sudden nuclear attack made Qing collapse to the ground, rubbing
her head.

She rubbed with such vigor that it almost seemed like she was trying
to start a fire, to the point where one could expect sparks to fly from
her head.

"Ack!"

"Why is a girl so indiscreet, walking around with her hips swaying like
that? It is already big enough to be a hindrance, yet you still dare to
strut around. Where did you learn such bad habits?"

When the heel was lifted, the pelvis naturally tilted back, causing the
buttocks to protrude.

Meanwhile, since the center of gravity moved upwards, the pelvis
moved greatly from side to side to maintain balance.

As a result, her posture was completely different from the graceful
walk emphasized by Ximen Surin. It was closer to the alluring gait of a
femme fatale trying to seduce a man.

"It's not like that. It's because, aack!!!"

SMACK!!!!

As Qing was taking off one of her shoes to show her, another nuclear
strike landed, causing her to roll on the ground.

Originally, a nuclear strike required a second one because the first
was never enough to make someone come to their senses.

"You dare to expose your bare feet in broad daylight, you wench?!
Cover them up immediately!"

"Ugh, Master, it hurts, it really hurts. I think my head is splitting open……"

"Hmph. It would do you some good for your head to split open a bit.
Stop that and get up. Cover your feet immediately."

Since acting pitiful didn't work, Qing quickly put her shoes back on.

Then, as she had something to say to her teacher-

"Ah. Master, do you perhaps know of the Dragon-Elephant Prajna
Heart Sutra?"

"Hmm? You mean the Dragon-Elephant Prajna Palm? Isn't that a Divine
Art of the Lamas? Originally, it was said to be from the Great Thunder
Sound Temple of Tianzhu. Why do you ask? Oh, did you pick it up
somewhere again? This time, you have picked up a truly excellent
Divine Art."

Ximen Surin was no longer even pretending not to know.

"It wasn't that. Great Master Wunue taught it to me."

"That bald monk? That can't be. Why would he teach you another
Qi Cultivation when you already have the Zhu Xiang's Heart Cleanse
Mirror? Unless he knew of your strange constitution."

"He told me to recite the sutra after telling me he could see through me
with just a glance. He told me to only recite the sutra, so it didn't seem
like he intended to teach me the martial art itself, though."

"Ha. If he was going to teach, he should have done it properly. Anyway,
reciting the sutra can suppress Heavenly Slaughter, so… Wait, that
bald monk could recognize Heavenly Slaughter? Did you show him
your pulse?"

"He just said he could tell by looking……"

Ximen Surin realized the difference in their realms.

In fact, as one's realm increased, each step was like a cliff leading to
the end of the world.

The few steps that Wunue had taken further might seem like a small
distance, but in terms of height, it was an unfathomable difference.

"Haaa. This master was careless."

Meanwhile, the Dragon-Elephant Prajna Heart Sutra meant a study to
protect the body and mind with the wisdom of dragons and elephants.

Here, the Heart Sutra did not mean the mind, but the heart, a
characteristic unique to this Divine Art, which connected the body and
mind as one.

For ordinary martial arts, the Heart Sutra would refer to the study of
Inner Qi and the Body Sutra would refer to the study of Outer Qi, but
only such supreme Divine Arts combined the two.

But what was the wisdom of dragons and elephants?

When dragons and elephants faced adversity, they broke through and
pushed forward. As such, it also contained a study to protect the mind
with an unwavering will to push forward.

However, it was more renowned as a Divine Art that bestowed divine
strength like that of dragons and elephants!

It was said that upon reaching the Great Accomplishment, one could
exert the strength of ten dragons and ten elephants.

Of course, martial arts sutras were nine parts exaggeration and one part
bombast. However, the effects alone were clearly conveyed.