\chapter{Great Instructor Ximen Qing (3)}

This guy was serious. Not that he's that serious, but he's the one who caught him.

It would be impossible for them to sneak through the Alliance warriors who were on emergency duty after capturing the Imperial Court members.

So, rather than saying that they came in secretly or by force, it would be better to say that they were sent in from above.

``…Instructor.''

Wan Talu had a very hard expression on his face.

He always had a sullen and grumpy expression, or in technical terms, a sullen face, but he looked completely exhausted, which was unusual.

Perhaps he heard rumors about the assassin's identity and that the Royal Guard was targeting him.

``Um, that. I heard you were badly hurt. Are you feeling okay…?''

A chill ran down Qing's back.

\textit{What the heck, did he eat something wrong? I wondered if there is another person who didn't suit formal speech this well. The guy who had been so ill-behaved up until then suddenly had a change of heart, and now he's like this.}

\textit{Of course, after receiving such a lifesaving grace, people should be polite, but, um, it really doesn't suit him.}

"It's hard to say I'm fine, even with empty words. But I don't care. I was simply acting as an instructor should. Even though every inch of my internal organs were completely destroyed, leaving me in shambles, I don't care."

"Ah……."

It was a joke disguised as truth. Wan Talu fidgeted, at a loss for words, his lips twitched.

\textit{Well, where did all the passion that kept on growing go?}

\textit{Well, anyway, the bastard had a right to know why this happened, as the target of the assassins.}

But.

"Unfortunately, the following scene is not suitable for viewing by minors. Trainee Wan Talu will remain silent and listen. Do you understand?"

A slightly aggrieved look appeared on Wan Talu's face.

``Instructor, I’m turning eighteen this year too-''

"You haven't reach twenty, have you? If you were a woman, I'd consider you an adult, but a man is out of the question. You haven't even gone through coming-of-age ceremony yet. You're a total baby, a baby."

For reference, in the customs of ahongyuan, the age of adult for men was twenty, and that for women was sixteen.

Wan Talu's expression became awkward.

``Baby, don’t say that…''

"Right? It's a bit creepy. Anyway, this instructor's opinion is firm. Minors are not allowed to watch, but instead, they can listen. Do you understand?"

"…All right."

Anyway, Gaebyeokdagi has never been actually harmed by the assassin, so what grudge could he possibly have against him?

I got injured, and the innocent civilians also injured, but all the guy did was get carried away and get swayed back and forth.

So Qing opened the iron door of the Tai Lingfan private cell again.

Behind the creaking iron door, Wan Talu's bewildered and slightly hunched figure was hidden.

It's true that the darkest place was under the lamp and the hardest to find was behind the iron gate.

As soon as she open the door, she saw the figure of Tai Lingfan sitting cross-legged.

In front of him, Jang Cheon-ho was hanging limply, clinging to the iron bars, but somehow he was very quiet.

Jang Cheon-ho, who kept making grunting sounds through his open breathing hole, was originally a dead person who did not speak or make any noise.

Qing chuckled as she looked at Tai Lingfan's wet hands.

"Wasn't he a subordinate you cherished? A murderous wretch, a leader who would strangle his subordinates? Truly a character befitting an assassin."

The corners of Tai Lingfan's eyes twitched at that.

Not only the corners of the eyes but also the hands placed on the knees trembled slightly.

'Master Tai, kill me, kill me, please.'

\textit{It was the disciple's last request, his skin peeled off and his familiar facial features now gone.}

\textit{Besides, this whole situation was probably what that horrible woman wanted.}

\textit{Why would she have shown me how to have him talk by blocking his breathing hole in front of me?}

\textit{But it couldn't be helped.}

\textit{It would have been better to send him away quickly than to leave him to die in agony. He himself had so desperately wanted to beg for it, so how much more difficult and painful would it be for that poor thing to beg for his own life?}

"Now, would you please tell me? What on earth did my trainee did that warrants the direct threat of the Royal Guards personally dispatching themselves to kill him?"

At that, Tai Lingfan kicked and bursted into laughter.

What the heck, I looked at it and it looked like a wrapping cloth, but I should have started by taking the skin off one arm and throwing it to him to use as a wrapping cloth.

It was a time when Qing frowned.

``Kuhuhu, haha, hahahaha!''

Tai Lingfan bursts into laughter.

He was so funny that he slapped his thigh and burst into hearty laughter for a long time.

Suddenly, as if nothing had happened, he turned serious and glared at Qing.

"Having experienced the tyranny of those rascals who call themselves the martial artists, I now know that His Majesty is truly right. Those who were born, raised, and still live by the grace of the Emperor dare to treat his subjects this way. Aren't you all treacherous traitors, utterly devoid of any sense of loyalty?"

\textit{If it weren't for the person who was listening, I would have called the Emperor a bastard at the end of every sentence to make him even more angry.}

\textit{There were ears listening behind me, so it would be awkward for an instructor to openly curse the Emperor, and it wouldn't be pleasant for minors to hear either, right?}

"You claim to be a subject of the Emperor, yet you use the Emperor's name indiscriminately and use it as an excuse to commit evil deeds, aren't you they traitor? Or are you saying that the Emperor personally ordered the secret execution of the Tongjeongsa's son?"

``Yes! That’s right! That exactlt what the Emperor has commanded!''

"It's not even funny. Why would His Majesty ordered to dispose of someone secretly when he could just point his finger?"

``Isn’t it because of a horrible murderer like you!''

Tai Lingfan cuts off Qing's words and shouts.

"You martial artists are just ungrateful lynxes, you horrible beasts! Why on earth do you exist? Do you cultivate the fields and grow the food that feeds the world? Or do you travel the world like a merchant, carrying goods? Or do you toil like a soldier, blocking the enemy and preventing war?"

All a martial artist did was focus on martial arts and only focus on his own strength, and he was of no help to any living being under heaven or on earth.

I'm glad it doesn't help.

They were a group of thieves who break the law, carry weapons, kill people without hesitation, and steal other people's property.

Even though there were government offices and soldiers, they intimidate the common people and collect protection money privately. If this was not thieving, then who is?

On the other hand, they claim that official duties were inviolable because they know nothing about the laws of the country. Isn't this an open statement of refusal to rule the country?

So, you can see how much he despises the laws of the state, this country, and its master, the Emperor, from the bottom of his heart. Doesn't the history of the terrible, unspeakable presumption, in which the reckless Emperor, the Emperor, dared to invade the palace and seize and shake the precious body, prove this?

In fact, it sounds right to Qing.

It's not that it's a bad thing, but if you think about it, it's not like it's wrong.

That's right, the martial arts world was called martial arts because it's so cool, it's just a land grabbing game for private armed groups.

But, even if it's the right words, it matters who says them. It's not something you want to hear from someone like this.

"A thief scolding a thief. The common people say that officials are more fearsome than the plague or the cavalry. You're not going to say anything like, 'The current officials arere doing a good job,' when you should be able to count on one hand the number of honest and clean officials in the world, were you?"

"You idiot! Do you think that state affairs are so simple, with everyone laughing and laughing? One decision leads to another, and another cries. Those who benefit take credit for it, while those who suffer losses blame the state and raise their voices! So, there's no official in the world who hasn't been criticized. How dare you, a thief who's never even worked in state, say such foolish things!"

Have you ever worked in government? Officials get slammed for doing something wrong, so all officials in the world were treated the same way.

Qing was speechless.

So have you ever done any work for the country?

When you reach the Tai Lingfan level, you won't have to feel aggrieved by power, and you won't have to feel sorry about money, so how would you know what the people were like?

But saying things like this to a guy like this won't work.

In Zhongyuan, those who carry the imperial mandate behind them were truly invincible. Since the mandate of Heaven was there, it was unconditionally right, and anyone who challenges it becomes a lawless traitor.

``Then what about the man who burned the Emperor’s people, threw firebombs at the Emperor’s people, and harmed innocent women in an attempt to save their lives?''

"It's a royal decree! It's a great undertaking! How can you accomplish something great by worrying about such trivial matters? Are you a fool who can't move forward for fear of stepping on a bug?"

"Hmm. This is… well, let's move on. Anyway, um. I guess we can move on."

He's going to die a miserable death anyway, so there's no reason to be angry about that piece of shit.

It's only natural to be angry when someone you can't kill starts talking nonsense. If someone you've locked up in a cage with your danjeon emptied starts talking nonsense, you'll just have to wonder if they're still that confident.

By the way, I think I've heard the same thing before.

Those were the kind of things that only the kids who talk about great causes and great undertakings say, that small sacrifices were natural in big things, they're such fucking assholes.

``So, why do you want to kill my trainee? If the Emperor wanted to kill him, he could have just issued an edict for him to commit suicide. But instead, he had the Royal Guards disguise themmselves as an assassin and secretly… hmm?''

Why must we kill secretly?

To hide the fact that he killed her.

Why hide it? Why did it have to be hidden?

When I asked why the emperor gave such an order, he immediately got angry and replied that the martial arts people were trash?

He did it because he hated the martial arts people, that is, he did it to harm the martial arts people.

Suddenly, old memories flash through Qing's mind.

At that time in Sichuan.

The emperor killed the prince and tried to shift the blame to the Tang family, so it was a plot to immediately accuse them of treason and punish them.

The son of the Tongjeongsa died after entering the Uijeongmuhakgwan.

If you insist that even though you were killed by an assassin, the assassin was also a martial artist, you could say that you were caught up in the troubles of the martial arts world.

It could be that they were planning to use this opportunity to investigate and punish all those involved, or they could be ordering the disbandment of the Jeongpa Moorim Alliance.

``You’re going to kill my trainee and blame Wulin, even though they're innocent, or rather, since they don’t seem to be innocent at all, so you’re going to blame Wulin for the crime?''

``Hehehe, you managed to escape this time, but since it’s the Emperor’s will, how long do you think you can keep doing this? You’re already as good as dead. Hehehe…….''

That was the moment.

``Is that, is that really true?''

Unable to bear the bird, Wan Talu jumps out and asks in a trembling voice.

I clearly said that it was not suitable for minors, but I couldn't help but think that he was a really disobedient guy.

But, look at this kid?

Even when he got hit by me, he would still speak informally to me, but he only became polite after I owed him my life.

Since the opponent was Tai Lingfan, you naturally start speaking politely to the guy who was trying to kill you?

It was a little, no, not too much of a bother.

But I'll let it slide this time, because I feel bad for you.

It's not that it's not, but the trembling eyes and the corners of the eyes and mouth don't look like they're in shock at all.

Well, since he was the son of a high-ranking official, even if his personality was a bit odd, he might have been loyal to the royal family.

If such a royal family were to throw me as a sacrifice, I would naturally be shocked.

"Oh, Young Master! You're here! Good! Get rid of that reckless woman! She foolishly embraced the Heaven-Shaking Thunder Bomb and endured the blast alone. Even though she looked fine, she's already seriously injured!"

``Instructor? Embraced the Heaven-Shaking Thunder Bomb…?''

Wan Talu looked back at Qing.

Qing scratched the back of his head awkwardly.

``No, that guy threw a fire bomb right in the middle of the market.''

Wan Talu's eyes were wide open, and he was dreaming again.

\textit{Embracing the Heaven-Shaking Thunder Bomb? How does her body is still intact?}

\textit{I heard that she was seriously injured, but she was here alone and speaking normally, so I thought it wasn't that serious of an injury.}

However, there's one big question for Wan Talu. What exactly does throwing Heaven-Shaking Thunder Bomb at the market had to do with embracing and dealing with it alone? Isn't it enough to just kick away or duck down?

If Qing could read his mind, she would have been amazed and scolded, 'As expected of a government official's son, he really has such a bastardly mindset. He can't even imagine that civilians would be harmed if a bomb explodes!'

Then Tai Lingfan urges again.

"Now, Young Master, haven't you heard? The Emperor has ordered you to kill that vicious traitor, that murderous bitch. No, first open the iron bars. I will personally finish that bitch off."
