\chapter{Great Instructor Ximen Qing (7)}

The outing was a consideration of the school to soothe the tired mind and body from studying and to allow them to focus on training again.

So, just because you're out and about all day doesn't mean you're going against the original intention, and even if you're going to be wild, it's just a bit of a change of pace, a personal choice.

However, in any group, there were bound to be those who stand out, and not everyone carried out their original intention of going out so obediently.

``Wow, coming down to the secular world, the air feels different already. The smell of people living here, ugh, yes, the musty scent of the green room was already very… Wow, my appetite has been whetted.''

Blue square.

In other words, it was rotten tofu or stinky tofu.

It was said that the food served on the emperor's table was called rotten tofu because it was not dignified, and that it was given the luxurious name of Qingbang because of its bluish, angular shape.

It was also the soul food of the people of the Zhongyuan.

Even after eating the world's best omnivorous woman, Heavenly Blossom Sword, she said, "It's frustrating, but it's delicious."

However, the evaluation of a beggar who lived by picking up bugs was that any food was delicious and there was no food that was not delicious, so it has no authority.

"Come on, let's have a drink first. Let's have a drink and think about how we can have fun."

Then, one person steps forward, looking embarrassed.

The youngest in the room, Jo Hyeon-il, was usually quiet, gentle, and docile.

``Hyung, I’m sorry, but I have some personal business to attend to.''

"Hmm? Personal business? Oh, by any chance? This guy, he's acting so well-behaved like a sage. He's a real womanizer. Is it really that urgent?"

``Uh, um? Oh, right. So, Hyung Ahn, I’m off now.''

It was when Jo Hyun-il was about to leave in a hurry.

Hyung Ahn grabs his shoulder and holds his chin.

``Wait a minute. Let’s go together. Since you’re in such a hurry, I’m moved.''

``No, that’s not it. I have an appointment with someone I know.''

"Do you know anyone? You're from Zhejiang, aren't you? How did you have an appointment here? And how did you know my schedule and make the appointment?"

``Well, it just so happened that way.''

``Hmm. Little brother Joe, something’s suspicious.''

Brother Ahn narrows his eyes.

At that, Jo Hyun-il gulped. His eyes rolled.

At that sight, Hyung Ahn laughed out loud.

"This guy, it looks like he seduced another woman during his entrance exams. Why, did he say he'd get engaged once he secured a position in the Wulin Alliance? Oh my, how did you hold out so longingly for her?"

``Ha, haha, right, that’s right. Hahaha. Well then, that’s it.''

Jo Hyun-il was about to leave again in a hurry.

Another brother grabs his shoulder again.

"No, you bastard. Are you being so cruel? You're not even going to introduce me to your sister-in-law? It's such a wonderful occasion. Are we supposed to keep it to ourselves? Shouldn't we at least give each of us a gift?"

``What, that, that. That’s not it.''

At that, Jo Hyun-il swallowed again. His eyes rolled again.

What saved Jo Hyun-il was another official in the same room.

"Oh my, oh my, Brother, here you were again. You said you wanted to go alone. Be more mindful of your surroundings. Brother Jo, hurry up and go. Brother Ahn isn't a bad person, but he's a bit tactless."

``Uh, well then, that’s it…….''

Jo Hyun-il, who was finally released, mutters as he walks away from the place.

Anyway, that clueless kid keeps holding on to people and making things difficult for them. He's like a dog.

The term "Hanjeo" means "pig" and was a serious derogatory term that insults the Han people.

Contrary to the people's assessment that he was gentle and docile, his true intentions were quite sinister.

Even muttering constantly.

Anyway, aren't you bastards, a people who devour everything with ugly greed like pigs, a filthy nation, the filth of the world that should be wiped out?

The place I arrived at, muttering curses under my breath and not hiding my discomfort, was a shabby house in a corner of Nosan County.

A person sweeping the yard in early summer, wearing a shirt that was exposed and dirty pants that were roughly sewn together, was startled by the sight and runs towards the visitor.

And then, bang!! He kicks my shin hard.

"evil!!"

Jo Hyun-il grabs my shin and collapses.

The person sweeping the yard frowned.

"You idiot, haa, why don't you come in right now!? What were you so upset about, and were you out of your mind just because you came outside?"

If Qing had seen it, he might have exclaimed, "Hey! This kid!"

The person sweeping the yard was Danjoya from Gary County, Guizhou, who had failed the entrance exam for the Department of State Affairs.

Jo Hyun-il shuts his mouth tightly and, with a somewhat sullen expression, opens the door that looks strangely new among the dilapidated thatched houses and goes inside.

Danjoya clicked his tongue and sighed.

Are you saying I should trust a guy who can't even hide his feelings properly?

Why, out of all the applicants for the civil service examination, out of the dozen or so, did it have to be this guy, and these guys again?

Out of fifteen people, there were only three, and among them, they were the three with the lowest qualifications.

Even if he had no luck, how could he be this unlucky? It was as if he had deliberately chosen only those who were lacking. Of course, judging by the fact that the Wulin Alliance did not know his true identity and had not responded until now, it was unlikely to be that kind of thing.

Danjoya's guess was that the ugly Hanjeos chose the underlings who looked naive and easy to use as slaves or expendable items, pretending to show favor.

After a while,

Four men crowded into a narrow earthen room.

The only windows that were there were blocked with mud, and even the new doors were thick enough to prevent even the loudest sounds from escaping. It was a truly suspicious interior.

The only problem was that it's summer now.

It was already a hot summer, and with four men sitting in a tightly closed space, it was truly suffocating and sweat was pouring down like rain.

There will be no need for a separate steam room.

``Well, Your Majesty. Isn’t it a bit hot…?''

"You punk, you're just complaining about the weather? Phew, even at this very moment, think of your fellow blood relatives who were being persecuted. Phew, those vile Zhongyuan people were oppressing you, starving to the point of not even being able to control your own body… Phew, unable to move…"

Even though I sweated a lot during my speech, it wasn't very effective.

Looking at the officials with somewhat sullen expressions, Danjoya once again speaks passionately.

"You, remember your life in the valley. Are you so intoxicated by the comforts of those Zhongyuan pigs that you find this mere heat, ugh, uncomfortable? Why do you think you can live well by siding with those oppressors and persecuting your fellow countrymen?"

``No.'' ``No.'' ``No.''

Somehow the answer was lackluster.

Even after Danjoya said that, he was like, "Oh no. They've lived a miserable life all their life, so it's only natural that they'd be intoxicated by the conveniences those Zhongyuan guys offer."

Danjoya's tone softens, as if he was soothing a child.

"Those Jeongpa bastards were the kind of people who would turn a blind eye to someone even if they're our closest friends and stab them in the back. You've already committed your crimes, so if you're caught, you're as good as dead. Now that you've embarked on such a dangerous mission, wouldn't all of our compatriots be praying for your safety? You were the hope of your compatriots—yes, our hope."

The expressions of the three officials become somewhat solemn.

Not stopping there, Danjoya felt around on the floor, lifted the floorboards, opened a hidden storage space, and took out three wooden armors.

"This isn't just talk. Now, take this. This elixir has been created by the Demon King and the Venerable One to reward your hard work."

The eyes of the officials light up at the word elixir.

Of course, if a martial artist hears of an elixir, they would jump out of their sleep. What good was mere sleep? Even if they were dead, they would jump out of their sleep, take it, and then die again. Wouldn't they be so delusional?

Danjoya opens the wooden box and reveals its contents.

A large, blood-red pill rested on golden silk, its lustrous red color gleaming ominously.

The officials were blankly staring at the bright red light as if they were entranced.

The door closes with a thud!

"You too can see this brilliance and size. It requires the help of a master to feed. It's an incredibly arduous and difficult process, taking two full hours, but for your hard work, can't I do something for you?"

``Daeju……!'' ``I believed in you, Daeju!''

Now, the three officials' expressions were filled with loyalty.

Danjoya nods her head and puts on a very solemn expression.

However, because sweat was beading up his entire face, from his eyebrows to his nose to his chin, the solemn feeling had faded considerably.

"With this elixir, your martial arts will also improve by leaps and bounds. You must curry favor with the Hanjeos and win their favor. If you act as harmless, docile, and obedient as possible, and if your talents were exceptional, it won't be difficult to secure a high-ranking position in the Wulin Alliance."

``Yes.'' ``Yes, sir.''

"Of course, this was a long-term goal. There were things you need to do right now, but for now, your absorption of the elixir comes first. Jo Hyun-il, you go first. You two, stand guard outside."

``Yes, my lord!'' ``Yes! my lord!''

The two who were behind in line looked a little disappointed, but they obediently got up from their seats and headed outside.

Just as I was about to go out and close the door-

"for a moment."

``Yes, my lord.''

``……Leave the door open.''

It was summer… … .

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing may seem lazy, always rolling around and lounging, but he's actually a man who believes in diligently doing his assigned tasks. When he does, he's often diligent.

And the same goes for the head, its intelligence can be somewhat misleading.

However, Qing was not a bad person who can't use his head, but rather a person who doesn't use his head.

My child was smart, but he was the typical example of a person who was smart when he does something but doesn't do it.

Even if there was a lot of pressure, the memorization ability to cram Buddhist and Taoist scriptures into one's head, and even the Confucian scriptures memorized later at the Academy, was that not a feat that an ordinary mind cannot achieve?

It was an obvious fact that Qing's mind was clear!

Add to that an innate eye for people and an eye for detail, and memorizing people's faces and names became a breeze as long as you had the interest.

Of course, since Qing doesn't like to think too much, he doesn't really think about it.

If you add to this the fact that you have a strong sense of responsibility and a sense of duty as an instructor, memorizing the faces and names of the officials was not that difficult.

So, observing, it's nice to say observing, but it's closer to meddling because you're sick and only talking, but looking after the officials through class, huh?

Qing sees people a little differently.

By reading the flow of the atmosphere, we can observe the human form in its full volume and mass, so we can say that we were seeing the world through the three axes that make up the world.

Also, you can see the numbers above your head.

And now, the number floating above the official's head is, huh? What's going on?

When I was doing my job as an examiner, didn't I write something on the evaluation forms of applicants who had over 100 bad karma or were close to it, saying that I felt bad about it and that I should re-examine it?

The school administration accepted Qing's opinion without hesitation, and since it was obvious to anyone that he was a member of the royal family, they sent everyone back with the exception of one person who had passed, saying, "Next time."

So, among the officials, there was no one who had any particularly bad karma (except one).

But today, it suddenly appeared.

Three of them, too.

No, look at these kids?

What, your bad karma increased by fifty points?

What bad things did you do when you went out?

Qing's eyes narrow.