\chapter{Great Instructor Ximen Qing (14)}

``Meet Mafu!''

Jo Hyun-il falls to the ground and shouts.

It wasn't an unexpected appearance.

When he heard that the Sosumahu had arrived a day after he had gone out, didn't the chief of staff say that it couldn't be true and was very flustered, saying that he would look into it?

That's why the Heavenly Blossom Sword was injured, so if you think about it a little, you could imagine that Mahou was nearby.

The little prince just looked down at the crown prince with a shadowy old face.

The expressionless old face, devoid of any emotion, the grotesquely swollen old flesh and deep wrinkles, were strangely unfamiliar, like some kind of monster rather than a human being.

Jo Hyun-il trembled involuntarily at the strange feeling that it was not a human face.

A devil like a painting, a bizarre appearance as if wearing a turban, a truly inhuman appearance worthy of being called the greatest demon in the Zhongyuan!

That's only natural.

Because I'm really putting on a brave face.

After a few minutes, Qing, who had turned over her head and was holding her chest tightly, asked in a fake voice.

"You rascal. Who in the world would bow like that? Do I have to bow so deeply without even knowing who I'm bowing to?"

"Yes, yes! My name was Jo Hyeon-il, born in Jomilgok. I, I belong to the Taedaesiksiminwoldan led by the great master, Seopsimma Hwang!"

The reason Jo Hyun-il emphasized the Subsimma Hwang was because he had heard of the infamy of Sosu Mahou.

He was generous to women and often shows mercy even to people from the Zhongyuan, but he was said to cut down men even if they were his followers if they bother him even a little.

So, it was a bold attempt to save myself by using the Subsimma Hwang as a shield.

After a few minutes, the man with the cotton swab turned over and his bare chest tightened, his bare eyebrows trembled.

Since it was a face mask made of existing materials, it was not sophisticated and cannot reflect the subtle changes at the eyebrow level, so when others see it, it just looks like you were staring blankly with a shadow.

Oh, this kid, he was a real blood cult kid.

Why on earth do these blood cult kids keep popping back out no matter how much I catch them? There's no place they don't get stuck.

Should I sweep it away?

You can just throw away the slaughter.

But, um. Before that.

"Huh. So what's the big deal? Are you the Demon King? No one should know about the secret activities of the Crown Prince, and the dead don't speak. Why should I blame your fate for catching my eye?"

``Oh, no!''

``Why?''

``That’s it, I’m on an important mission!''

``Huh. Are you on a mission?''

``Yes, yes, that’s right, that’s right, that’s right. My life was of no consequence, but for the sake of the great cause of the religion, for the sake of my long-cherished wish, please…!''

It was a truly unconvincing argument.

A guy who was shaking and has no control over his eyes because he doesn't want to die should be saying something like that.

But isn't there anyone in the blood sect?

The scheme to infiltrate them may be great, but to infiltrate such a stupid, cowardly, and foul-mouthed guy.

Blood ties can be unfair.

All the smart ones were eliminated, so who was to blame? It was Qing, who had written the evaluations solely on bad deeds, who was the culprit.

I cut off all the smart people and only brought in people to be porters, odd jobs, and errand boys. What's wrong with that?

In addition, the Shiksimdan was lacking in talent.

Because the Hangzhou branch, which was the center of the Shiksimdan, was destroyed, weren't all the excellent blood demons and blood demons that were being produced, as well as the producers and high-ranking warriors, all swept away at once?

Even that was ultimately due to Qing's activities.

So the blood sect will be wronged.

No, you yourself were the one who put out the cuts and then you ask why there were no talented people. What was your state of conscience?

"Huh. Let's hear it out loud. If it's truly an important mission, how could I be so harsh?"

"That's the infiltration of the Wulin Alliance! The mission was to ascend to a high-ranking position in the Wulin Alliance, spread loneliness, and poison the Wulin Alliance bastards. If this mission succeeds, wouldn't we be able to wipe out the Wulin Alliance bastards in one fell swoop?"

"Ha, how funny. How did you manage to rise to such a high position in the Wulin Alliance? Even in this small academy, someone who loses the hearts of the people will likely rise to such a high position. Rather than fail needlessly and raise the Wulin Alliance's guard, wouldn't it be better for me to sort things out here myself?"

"No! No! I've already offered the precious elixir to Heavenly Blossom Sword, so wouldn't the Jeongpa bastards be willing to do as much as they've received? We also have elixirs to give to Hakgwanju and Hyeonhwa, so shouldn't we be able to secure a spot?"

This was why a political party was a political party.

Bribing the officials and the Safa people didn't yield much in return, and if something went wrong, they would most likely shut their mouths and pretend not to know.

But what about the Jeongpa Unmanned?

As befitting a knight of the upright party, he makes sure to pay for any bribes he receives. How fair and just was this the attitude of a gentleman?

The question of whether a gentleman doesn't accept bribes was not valid in the Zhongyuan.

In the Zhongyuan, bribery was a legitimate means of communicating opinions, a demonstration of financial power in response to military force, and also a natural act of good faith and courtesy.

The country encourages bribery in the first place.

The salary of an official was not enough to support a family, so the emperor's deep intention was to make up for the shortfall by accepting bribes.

Qing was silent for a moment.

Of course, the headmaster was the headmaster, and didn't Chunfeng boast during the entrance ceremony that as the head of the Wulin Ohwa, he was in charge of the central academic administration of the school?

If you're going to bribe them, those two would be the perfect fit.

But, that bribe contains loneliness.

That won't work.

Qing rolls his head for a moment, then makes a mock angry voice.

"You, you dare to say you're benefiting the enemy now? By feeding them elixir? Now that I think about it, it's not you who's becoming a spy, but rather a spy from the Wulin Alliance."

It was an awkward anger that was a beat too late.

But even that awkward anger becomes a heart-pounding fear, not a sense of discomfort, when it was done by a master who holds the power of life and death.

"No, that's not true. That's a misunderstanding. The elixir was elixir, but I heard it was given by the Venerable One because it contains loneliness."

``That’s an excuse. Tsk. Enough. Okay.''

Qing holds out her hand.

Jo Hyun-il's expression was one of bewilderment.

He didn't suddenly extend his hand to me, so I wondered why he was extending his hand.

``What were you staring at? I’ll feed it to you myself, so why don’t you give it to me?''

``Oh, Mahui, our mission is….''

"You idiot. You don't know how suspicious the martial arts world is. Offering elixirs as bribes? They'd obviously find it strange that you'd offer them elixirs from somewhere. Surely you wouldn't be barking out nonsense like you came down to me as a family heirloom, would you?"

Jo Hyun-il flinched at that.

Didn't that dog already bark?

Qing clicked his tongue.

"Tsk tsk, you second-rate punk now, you keep an elixir as a family heirloom? It's like a dog quitting pooping and a gambler quitting gambling. Even if you entrusted the fishmonger to a cat and the mill to a sparrow, you'd be more trustworthy. Would you, with such a family heirloom, not eat it and be full?"

``Oh, it worked on the Cheonhwa Sword.''

"Tsk tsk. That girl was still young and ignorant of the ways of the world. But do you think she'll be able to get through to the worn-out Kwan-ju and that smart Hyeon-hwa? And where does Ga-bo keep coming from and passing on the knowledge?"

``Well, the three of us should each go…''

Jo Hyun-il trailed off.

Now that I think about it, it sounds strange.

Qing's eyes widened, the three of us, that means there were still two more left.

These days, the three of them were hanging out together, and all three of them have suddenly improved their skills.

So, it was Bang Yun-eol and Jang Jeo-sam?

Are those two guys outside right now that guy?

``Are you talking about the two guys outside right now?''

Then, only then did the two people quickly rush into the warehouse.

``Ma, I see you, Mahu.''

``I, Jang Jeo-sam of Jang Mil-gok, would like to offer my greetings to the Mahou.''

``Ah! I am Bang Yun-eol of Bangmilgok.''

Milgok means a hidden valley, so if you add a surname in front of it, it becomes a hidden village.

The same principle applies to Zhangjiajie, Yuanjiajie, and Yangjiajie near Tianzi Mountain.

It was a typical village of traitors, and it was also a village where descendants of traitors live together because they cannot go outside.

They had appeared to deal with the enemy at the time, but the fearsome Sosumahu was there, so they were both hiding, unable to do anything.

Now that they're mentioned, what should I do? I should first say hello.

In fact, a master of that level would have noticed their clumsy movements, so they should have heard it right away.

If that was the judgment, I wouldn't have been drafted into the role of infiltration team porter.

Qing nods calmly and asks.

``Are you all there? The rest?''

``The leader of the group was currently staying in Laosan County, or rather, was staying there, and the rest of the group has returned to Guizhou.''

But, these guys answer very obediently and quietly.

Of course, Qing would prefer to find out for herself through pain and fear, but isn't it too late to make a fuss here?

And since they firmly believe that I am a White Hand Witch, they won't talk nonsense.

Well then, isn't now the opportunity?

``Return? Are you talking about you?''

``The captain decided that there was no need for it any longer…''

Plans have changed.

The original plan of the Blood Cult was to have the elite combat unit of the Shiksimdan enter the school, and then, with internal support, to wipe out the entire school in a large-scale attack.

However, since there were only three people inside, and they were not enough to meet the level of power, Danjoya judged that internal support was impossible, and chose to vent his loneliness in the Wulin Alliance instead.

Qing sympathized with him.

It would be difficult to attack with these guys, of course.

Look at it now, if you just hit it, wouldn't a whole lot of information come pouring out?

It just gushed out like water from a leaky dam.

Then what? When the water comes in, you have to row the boat. You have to really get the hang of it.

Qing's eyes were dazzling.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing looked down at the two wooden boxes in his hands.

The elixir confiscated from the other two was a elixir containing loneliness.

But now it's my elixir.

Anyway, if loneliness was to be felt, the bottle of alcohol will be eaten as a special treat, and then only the pure elixir will remain.

I was already wondering if I needed to go to Hyeon-gyeong to get my internal energy up, but now I'm getting these ownerless, free elixirs.

There was no such thing as a very profitable profit.

Well, I have to drink it once the bottle was uncorked.

First, the three idiots were sent back quietly.

I warned them not to tell anyone unless it was at least a certain level of Ma-Hwang, because if they dared to talk carelessly about my existence, I'd make them beg for my death. Well, they're still people I don't trust.

Well, it didn't matter what I said.

She's a fake White Hand Witch who doesn't exist anyway, so what does it matter whether she gets caught or not?

Besides, there's still plenty of time left until this car leaves, so it's like a rat in a trap.

What do you mean, the foxes were going to run away?
