\chapter{Great Instructor Ximen Qing (18)}

The Wulin Alliance was in Kaifeng, and for the people of the Zhongyuan, Kaifeng and Beijing were within touching distance, just a stone's throw away.

Especially if the ferry was a government ship, especially one belonging to the Imperial Palace.

According to national law, all horses were property of the state, so all the world's famous horses belong to the royal family. And these famous horses were bred together, and their offspring were then bred to produce more famous horses.

So, the messengers coming out of the palace and the messengers coming in ride the best horses in each city and run twelve hours a day, their speed being faster than any messenger in the Zhongyuan.

That's ultra-high-speed communication!

So, the journey of 1,500 li from Kaifeng to Beijing took 51 fine horses and 50 post stations, and it took only 14 hours to reach the royal palace.

That's right, the Forbidden City!

It was the greatest palace between heaven and earth, not only in the past and present, but also in the future.

However, the magnificent exterior of the Forbidden City was rarely even visible to the common people, as they had to first pass through the large wall surrounding the Forbidden City and its gate.

Tiananmen was the first gate of the Forbidden City, where nothing important ever happened in the past and the future..

Passing through Tiananmen, you reach the Wumen Gate, the gate of the Forbidden City. Passing through the Wumen Gate, you reach the inner courtyard, a closed garden on all sides, surrounded by high walls and armed with countless bows, crossbows, and cannons.

When you cross the flowing water and reach the other side, soldiers pour out of the tightly closed Hwanggeuk Gate to confirm your identity.

And when you pass through the Hwanggeuk Gate, you will finally see the Hwanggeuk Hall, the grand hall where the emperor receives petitions.

Behind the Hwanggeukjeon, there was the Chinese Hall, which was just fancy and has no particular purpose, and behind the Chinese Hall, there was the Geongeukjeon, which was used for holding large national ceremonies or holding large meetings.

However, there was a separate palace where the emperor's affairs were actually conducted. If you go along the left side of the Hwanggeukjeon Hall and pass through the three main halls of the Hwanggeukjeon Hall, Junggeukjeon Hall, and Geongeukjeon Hall, you will reach the simple building called Yangsimjeon Hall.

It may be because the Hwanggeukjeon and Geongeukjeon were so vast that they felt too desolate to conduct state affairs.

Or maybe it's just because Yangsimjeon was closest to Geoncheonggung Palace, where the Emperor resides.

So, the Forbidden City and the Hall of Conscience.

The emperor's chair was always on the steps.

Because the Emperor was the son of heaven and the one who represents the will of heaven, he was a god and not a human being, and was of a different class.

Therefore, the area above this staircase was like the heavenly realm above, a sanctuary that no one can invade.

This staircase that separates heaven and earth was called the Pye.

And below the lungs, twelve of the highest-ranking eunuchs and several of the eunuchs were always stationed, charged with relaying the affairs of the human world to heaven.

Therefore, if a mere human wants to report to the Emperor, he must first relay it to the eunuchs below the Emperor's level, and then send it up to Heaven.

That was why humans say this.

``I report to Your Majesty.''

I, the great Seokjong Wi, and the martyrdom of the Golden Knights have brought you news of the gang of thugs in the Gangho region. As commanded by the Emperor, I convey this to Your Majesty.

The eunuch received the letter, carefully climbed the stairs, bent down so that his head almost touched the ground, and stretched out both hands in front of him.

The emperor receives the letter, and his expression quickly decays as he reads through the text.

``You, you, dare, you reckless bastards……!''

The expression "rotting away" was not enough.

His entire face was so red that it was almost like a date, black and rotting, and the blood vessels were bulging out in a vicious manner, giving him an extremely rough appearance like a wall covered with bushes.

The whites of his eyes were bloodshot and his whole body was trembling, and he looked like a vicious, evil spirit, and was furious.

It looks like it would cause a grand explosion if someone just poked it with a needle.

That was the moment.

``Your Majesty, please hold on tight. I fear you may injure your body.''

A voice of unparalleled clarity flows out.

It was the sweet voice of a woman who made a sound like silk, and the gentle concern of a eunuch standing behind the throne with his sleeves gathered.

It was said that the voices of eunuchs who were castrated before the age of ten were indeed beautiful, but the face revealed beneath the hat was clearly that of a woman rather than a castrated man.

The eunuch who wrote the letter, Jo Wanggang, one of the twelve eunuchs, twitched his eyes, but he had already lowered his head deeply.

"Yes, you're absolutely right. That's exactly what these worms want. Phew…"

Originally, the Emperor did not speak directly, so the process of the voice of heaven reaching the earth was also something that had to be mediated by the people on the stairs.

However, that was just the way the palace rules work.

Why should I bother to put it down right away and then go back and forth and be so picky and fussy?

Although these ceremonies may enhance the emperor's dignity, they cannot prevent him from bursting into tears.

So, when we first met, we only went up and down the stairs once, and after that, we just talked normally.

The Emperor was also a human being, a human being!

The emperor sends letters to his subordinates and closest associates.

The ministers within the Hall of Conscience received the letters one by one, read them, and reacted with fierce anger, saying, ``These bastards… …! These people… …! This trash… …!''

The emperor's heart was quite comforted when he sees his subject venting his anger like that, thanks to his advanced worldly wisdom that has already become ingrained in him.

The letter was none other than the official announcement of the Wulin Alliance.

"Please, let's stop this. We can't stand it anymore. Look at them now. They've killed all their subordinates. It wasn't just us, but a few witches. Of course, we could have done it, too."

And the back page was a statement written by the intelligence branch in Hanam.

"We have confirmed that a major fight between a White Hand Witch and an assassin took place in Laosan County. The fact that there were multiple witnesses to the demonic witch's appearance makes it a credible fact.

There were many testimonies that the appearance of the White Hand Witch was dark and rough, and it was assumed that the demon's spirit has gone berserk, so the White Hand Witch's realm can be identified as a demon.

However, there was a rumor that the assassin's target was not a White Hand Witch, but the head of the Department of State Affairs, and after tracking down several groups of assassins, this was confirmed to be true.

It was claimed that a high-ranking official of the government requested it, but the identity of the person requesting it was unknown.

The first commotion was the battle between the assassin and the instructor of the martial arts academy, Heavenly Blossom Sword Ximencheong, but it seems that for some reason, a White Hand Witch also participated later.

There was a rumor that the White Hand Witch was repelled by the instructors of the Legislative and Military Academy, but eyewitness accounts of the process were rare and vary greatly from testimony to testimony, making it unreliable.

The repulsion of the White Hand Witches itself was likely a false rumor spread by the Wulin Alliance to promote their achievements.

This was intelligence gathered by the Hanam Intelligence Branch after the announcement of the Wulin Alliance.

It was a report written without knowing that the assassin's request was from the Imperial Palace, as there was no way a single intelligence branch would have known about the secret operation to assassinate the son of the Tongjeongsa.

"These guys, phew, what shall we do with these guys? These bandits, armed with weapons, were becoming more and more assertive, and the country was in serious trouble. How can we eradicate this disease?"

``Ahem. That’s how it is. Okay.''

``It’ll be a bit difficult right now……''

The subjects express their displeasure.

Well, the announcement from the Wulin Alliance must have been very clever.

I have a feeling that these guys have crossed the line by going to extremes to cut down the guards of the Golden Guard.

They didn't do it on paper, and it's all because of the blood sect, didn't they?

The Wulin Alliance may or may not be innocent.

Didn't you say that the fight between the assassin and the Heavenly Blossom Sword came first?

The Wulin Alliance was clearly aware that there had been an attack targeting the capital of the Uijeongmuhakgwan.

However, since the announcement completely omitted it and packaged it as a fight with the Blood Cult's demon leader, isn't that an incredibly ambiguous statement?

I really don't know why the White Hand Witch suddenly appeared and messed things up.

I don't even know why the Golden Guards were fighting the White Hand Witches.

So, the Wulin Alliance could have used the excuse of a White Hand Witch to dare to kill the emperor's man. Or, as Madu always does, he could have gotten into a fight over something trivial and gone berserk.

In the worst case scenario, it cannot be ruled out that they may have joined hands with the Blood Cult to carry out the work.

Ultimately, the exact details were unknown.

However, the Muring Alliance took advantage of this opportunity to raise questions.

Has the Wulin Alliance noticed the palace's plan?

If that's the case, then it means that we can no longer tolerate it, and the task of getting rid of those ruthless warlords in the Zhongyuan will have to be handled with even greater care.

If something happens again, what will happen if a group of bandits called Wulin rise up and do something?

If we mobilize the military, we won't lose, but it will only end up at the level of not losing.

``If you have a good idea, let me know without hesitation.''

Below the stairs, the people standing on either side of him make eye contact.

The fat old man standing on the left was the eunuch leader and head of the class, Jeong Sa-bo, who was a eunuch and a long-time enemy, and he was glaring at them with a mocking look.

How about it, do you have anything to say?

The thick-set man receiving those gazes, the muscular middle-aged man with the muscles around his neck, was none other than the leader of the Royal Guard, Admiral Bang Cheol-ryeong.

Because you're such a fucking old man.

Bang Cheol-ryeong clenches his teeth, making his already thick trapezius muscles even thicker.

At that sight, Jeong Sa-bo smiled faintly, then pretended not to notice and took a step forward with a serious expression.

"Your Majesty, it's all the better. It's the Heavenly Sword, isn't it? How about summoning him to the palace and offering him a grand congratulation?"

It was a eunuch's characteristically feminine way of speaking and a hoarse voice.

It might be a little off-putting coming from a fat old man, but what can you do, eunuchs were like that.

The emperor's expression hardens at that.

"What were you talking about? Chihara, you may not be able to subdue the bandits who run wild, unable to distinguish between heaven and earth, and who were wreaking havoc on the country. Are you saying we should praise them?"

``Your Majesty, how could I not understand your intentions? These were all words I offer with all my heart, for your sake.''

A lie was something that once you tell it, you have to tell a bigger lie to make up for it, so you can't take it back and it just keeps growing bigger.

That bandit group called the Wulin Alliance has dared to deceive the world with lies, so we cannot deny it even if we further expand their lies.

So, this incident, the fight against the great demon leader of the Blood Cult, was itself worthy of praise, and the Wulin Alliance cannot deny that Heavenly Blossom Sword was the representative of this.

"Your Majesty, isn't the Heavenly Blossom Sword a woman considered to be the next greatest in the world? Even the wicked Emperor Mu couldn't reach his peak at twenty. If left unchecked, wouldn't she be a source of great trouble?"

At the mention of the Emperor, a large vein rose again on the Emperor's face and anger filled him.

The sagging cheeks were lifted by the Jeongsabo.

"But no matter how exceptional her talents, she's still a woman after all. While we're here to congratulate her, wouldn't it be a pity that a woman in her twenties still has no match? How much of a blessing would it be if the Emperor himself personally arranged her marriage for her?"

"Huh? But don't you know how reckless the women of the martial arts world are? Even if I offer to take her on, how ridiculous it would be if she refused."

"So, you must make her an offer she can't refuse. Your Majesty, wouldn't she be a perfect fit for the Crown Prince's lady?"

Lady refers to the lowest rank among the Crown Prince's wives. After the Crown Prince ascends to the throne, she was promoted to the fourth wife, Bin, and receives a higher rank.

In other words, it was a proposal to give the position of royal wife to Heavenly Blossom Sword.

It was definitely an offer I couldn't refuse.

Who in the world would dare to refuse the position of the prince's companion?

Rather, it was something that all civil and military officials should rise up and oppose.

They should all lie down in front of Hwanggeukjeon and say, ``Please understand that I am entrusting the crown prince’s wife to a lowly butcher woman.''

Of course, the emperor was also so shocked that he felt like exploding.

``What, what was this? Are you suggesting that we bring that dirty thief who’s been swindling in the martial arts world into the palace? Have you finally lost your mind?''

The emperor shouts.

But Jeong Sa-bo was calm and only has a fat smile.

"Your Majesty, aren't you the next greatest in the world? Think of Emperor Wu. Once you become a royal lady, you can no longer devote yourself to martial arts, so won't you be in no danger?"

"That's it! That's nonsense! The eunuch must stop saying such outrageous things!"

"Your Majesty, Your Majesty, please acknowledge my loyalty. A woman of no lineage, a barbarian, entering the palace, who else could she rely on but her husband? Naturally, she would turn to the Crown Prince. Wouldn't that mean a warrior of the highest order would follow the Crown Prince?"

``That’s…, um.''

The emperor strokes his beard.

After hearing this, it doesn't seem so bad, does it?

"If you really don't like it, why don't you just get rid of it after a while? According to palace law, any evil sorcery used by a royal woman was punishable by death. So, who knows what kind of tricks a barbarian woman, blinded by favor, might employ? A mere martial artist wouldn't dare interfere with palace affairs."

Once the Heavenly Blossom Sword enters the palace, whether he kills or lives will already be a matter within the royal family, so there will be no need to worry about the opinions of the martial arts world.

"More than anything, this will be a stern rebuke to that bandit gang called the Wulin Alliance. No matter how much you try, you're still just ordinary citizens. How would you feel if you opened your eyes and saw your divine dragon stolen from you?"

At these words, the Emperor's scales tilted sharply.

I don't like the idea of bringing a savage, dirty woman into the imperial family, but how many times have there been non-political marriages in the course of ruling the Zhongyuan?

No, rather, weddings should be political.

Whenever the king gave his heart to a woman and married her out of love, the country would fall into chaos.

Dalgi was like that, Seosi was like that, and Yang Guifei was like that, so aren't there countless other evil women and the harm they caused in the Four Books?

And so, finally, the emperor nods.

``Good. I am relieved. The Admiral of the Palace will work hard to prevent any unpleasant incidents.''

Admiral Jeong Sa-bo, despite his chubby body, bravely bows his head deeply.