\chapter{Great Instructor Ximen Qing (1)}

The headquarters of the Admissions Office of Yizheng Martial Study Hall, underground prison.

If I had heard of it, I would have wondered why there was an underground prison in the main office of the admissions office, and if the connection was a bit strange.

And, in fact, it actually did.

No, that's right. If I were to call it by its hometown name, it's like the Jungwon High School dungeon, the Jungwon University dungeon, what's the difference?

But this was an action that takes the Zhongyuan too lightly.

Originally, the history of the Zhongyuan was a history of collective warfare and survival. It was not a martial arts world, but a Zhongyuan. If it was a communal house or a large estate, then of course a prison would also be designed.

Of course, it was not designed as a prison, but as a warehouse or a mine. This was the wisdom of the people of Jungwon, who use it as a warehouse when there were no tenants to reduce waste of space.

So to be precise-

The headquarters of the Admissions Office of the Department of Political Science and Law, basement warehouse.

However, it was designed as if it was a warehouse, but it was tightly blocked with a thick iron door on the top of the stairs and another thick iron door under the stairs, as if it were hiding some kind of treasure.

On the other hand, it was dark because no light comes in, and even though it was a warehouse, there were several small rooms separated from each other, and the small rooms were blocked on the inside with iron bars behind iron doors. No, this was just a prison.

Why was there an underground prison in the main office of the admissions office of the academy (omitted)

The front panel was in a mess, so it was a bit strange to hear the sound.

Although I was held like a princess, countless pieces of shrapnel were still embedded in my abdomen, stomach, and even my chest, so I kept my body very straight in a straight line because it would hurt if I bent over.

Murong Zhuxi carefully puts down the Qing.

It's strange because the body was stiff and straight, like putting down some kind of scarecrow.

``Hmm. I think it’s going to be a bit rough, but it’s embarrassing, so could you wait upstairs?''

"Are you alright? Your Majesty, you're not feeling well, but if it's torture, I'll help you. Leave it to me. Just say the word and—"

"It's okay. But, somehow, the wording was a bit off. And it's not torture, it's interrogation, interrogation. If you say interrogation, torture, it makes me sound like some kind of torture technician."

Well, it's not like people usually say things like, "I'll help you with the torture," or "Leave it to me."

But wasn't it Lady Mo Yong who trembled even at a simple human dissection that was nothing special?

But there was no such expression, only a very good hostility in her eyes, and it was as if she was burning with passion for anatomy, and the spiritual growth of Lady Mo-yong was dazzling.

However, no matter how great Lady Mo Yong was, it was something that could not be done.

because?

I need to have some fun too.

If I were to be entitled to this supreme pleasure of revenge in this current situation, I would be first, and that nameless girl, Wan Talu? A piece of shit like Gaebaldagwi would only be third.

"I'm fine. Don't sneak up on me and nod your head. You look like someone I'll be staying with."

Then Seol-i-ri turns her head.

He seemed to be really angry, so I wondered if he would follow me around like this all day. Whenever I spoke to him, he would turn his head away and maintain an attitude like, "Seol-i-ri was really angry."

What the heck, was Gunyeong acting more and more like a child?

Even Ja-yeo wouldn't do this. Even Jang-myeong, no, if it were Jang-myeong, he could do it. Did he get it from Jang-myeong?

``Don’t overdo it.''

The low voice of Pangdaesan was more of resignation than anger, a voice that says, "There's nothing we can do."

And the concern and worry contained therein makes Qing snicker.

"What's with the crowd? Can't we even eat the fish that's already been grilled? Okay, then let's go up and sleep. Same with Sima-lang."

Sima Chunfeng's eyebrows were crooked.

Sima Chunfeng, who had been hesitating as if it were difficult, finally opens his mouth to dissuade Qing.

A murderous slang, meaning to kill someone and silence their mouth. In the Qing homeland, it was also said that the dead do not speak.

Although it was an expression that the people of the Zhongyuan can easily say, whether they actually put it into practice was another story.

Things have already gone terribly wrong.

Since we have already become mortal enemies with the assassins who claim to be the Golden Guard, we cannot come forward and say, "Oh, you were working for the country. Haha, I didn't know. Sorry." and mend things.

So, even Sima Chunfeng had no choice but to agree to the extreme prescription of killing the mosquito, but no matter what.

``Heavenly Blossom Sword, even if you were Heavenly Blossom Sword, there was no need for you to handle this alone-''

"Hey, I've been through something like that too, so I'm just trying to vent some of my frustration. I'm fine with it, you know? I actually like it."

Qing interrupts Sima Chunbong.

Even if it's called the Heavenly Sword, it's probably just an abbreviation for a superior future leader like us.

Sima Chunfeng nods his head heavily.

There was a world of difference between cutting down an enemy in a life-or-death situation and killing a captive who has already been subdued and cannot resist.

Now, isn't Heavenly Blossom Sword saying he alone will bear the weight of the slaughter? He alone was enough to stain his hands with blood! (No)

Rather, you say it's good? You're not the type of person who enjoys killing with the greatest murderous spirit in the world (right?) With such a lame excuse, such nonsense. (I meant it.)

Sima-lang closes his eyes tightly.

I guess I have to accept that kind of heart of Heavenly Blossom Sword.

Of course, I haven't gotten anything right, but

"I may be ashamed, but I will accept your noble spirit. This time, it was your defeat. Truly. You. This time, I have no choice but to acknowledge you."

As Sima Chunfeng said this, he gave a bitter smile and a somewhat hot gaze.

Qing, um. What was this guy?

So the group turned around and heard the sound of the iron door closing.

The faint sound of the stairs going up beyond the iron gate, and after some time, the iron gate creaked shut again.

And then the son-in-law became quiet, and only the faint sound of the fire crackling in the brazier could be heard.

The blue face was clearly shaded in contrast, and glows with the flickering flames.

Daeyoungban was just quietly observing the interior while sitting cross-legged.

The pain in my lower abdomen was so cold that it was almost painful, and the cold evil energy inside me was slowly flowing through my energy channels.

The minority magician's minority poison, was truly a vicious and vicious infiltration method that lives up to its reputation.

Originally, it was an urgent internal injury that needed to be resolved by pressing it down with a bet, sealing it somewhere, then taking an elixir or seeking the help of a doctor.

But because the evil thugs of the martial arts world had burned a lot of mountain spirits, there was only a handful of internal energy left.

Since the mountain spirit had faded away, it was Daeyoungban who was trying to cultivate the handful of internal energy he had by diligently turning it over and increasing it even a little.

How much time has passed like that?

A thought suddenly crosses my mind.

When was the last time I cherished and treasured this insignificant internal energy, which was barely enough to last a few breaths, even though it was so weak and insignificant?

When I was just about to throw myself into the Golden Temple.

Iron Heart, thinking back now, even though my internal energy was truly pathetic, I was so happy back then that I vowed to become the greatest master in the world and serve the Emperor above all people and below all people.

Back then, he had been working hard, reducing his sleep and utilizing his internal energy. From then on, memories of his past, when he had never been lazy in his training, came to mind, and they came back to me from a much longer time.

Suddenly, Daeyoungban's eyelids slowly rise, revealing half of his pupils.

Unfocused pupils inside half-open eyes.

But his eyes were clear, and since the place they were looking at was not here, and not at this time, he traced his life from the past to the present—

Knock knock knock knock knock!!!

At that moment, a sharp sound shattered Daeyoungban's deep thoughts.

The focus of the Great Hall immediately returns, and the nervous gaze directed at the suddenly noisy visitor was soon tinged with surprise.

``How are you alive, no, how are you so fine?''

"I'm not fine. I think I'm going to die. Of course, my life isn't in danger, so I won't die. But anyway, Heaven-Shaking Thunder Bomb? It hurts a little."

Daeyoungban's eyes shake.

I thought it was just a last sprint before it died, because the image of the pitch-black mine leaping out of the explosion was vivid in my mind.

Qing snorts at him.

"But, no, what? What kind of enlightenment does a guy who abandoned his subordinates and ran away have? Oh, was that so, possessionless? Did you feel free after abandoning all your subordinates?"

Daeyoungban's face suddenly distorts.

``You bitch, you bitch!''

Daeyoungban's face turned pale in an instant.

"Okay. First, let me tell you something. You're afraid you'll succumb to the pain, so you'd rather bite your tongue than open your mouth. That's not allowed. If you do that, I'll make you regret ever being born. Do you understand what I mean?"

``Do you dare to threaten the Emperor’s subject?''

Qing giggled.

``Yes. Is there a problem?''

``How dare you, I have received the Imperial Edict, this is the will of Heaven, how dare you utter such a rebellious and outrageous thing!''

Qing just smiled.

And then she points upward with her finger.

"Now, do you see the sky above? It's enough to block the sky. How would even the Emperor's grandfather, let alone the Emperor himself, know what happened here?"

``You bitch!!! How dare you!!!''

``Okay. Calm down and listen.''

Qing coughed, then let out a groan she couldn't hide, then continued in an exaggerated tone like the author's storyteller.

"Suddenly, a group of ruthless assassins attacked the civilians. The righteous heroes stepped forward, slaughtered them all, and protected the peace of the world. Indeed, the Emperor is deeply pleased by the actions of these brave warriors."

``You bitch-''

"Keep listening. However, it's a pity. The assassins, who deserved the wrath of heaven and earth, have all had their heads shattered, so it's frustrating not knowing their true identities. Unless there are even some clues left to identify them, then who in the world could possibly know the true identities of these assassins?"

I'm going to blow your heads off.

I will also get rid of any items that could identify you.

So in the end, no one in the world will know your true identity.

The expression on Daeyoungban's face turned red and blue.

At that moment, Qing realized.

\textit{Ah, that's it.}

\textit{Why, in movies or TV dramas, when the main character is caught, the villains always babbled in front of him, revealing their true identities and plans.}

\textit{I never understood why he was so stupid and yet so kind, so easily revealing his plans and accomplices.}

\textit{Now I could understand.}

\textit{No, how can I put up with this?}

\textit{He's a guy who's going to be killed anyway, so of course he should be treated a little more unfairly.}

"First of all, don't bite your tongue. It takes a long time to make someone write by hand, and it's frustrating. If you do that kind of thing…"

Qing's smile deepens even more.

"You know what they mean by 'destruction of the clan'? Let's see. It looks like a few extremely evil witches will suddenly appear and wipe out your entire family before disappearing."

At that, Daeyoungban's expression becomes distorted.

\textit{Oh, look at that expression.}

It was a time when Qing was happily enjoying the crushing.

Suddenly, a loud laughter erupts.

"Even if you try hard to wear the mask of a villain, it's no use. The woman who sacrificed herself to save the innocent people at the market is now bluffing to commit a massacre. Even though you're trained in Demonic Art, you're still a Taoist. Your attempts are commendable, but all I can say it's laughable."

At that, Qing's mouth dropped open.

\textit{What? What the hell did I just hear? Did I, um, misheard?}

\textit{Well, you could say something like that, but still, shouldn't this guy not do that?}

\textit{How many innocent people would've been involved in the market? He filled that vicious grenade with his Qi and threw it at me, intending for me to die? What is he saying to me now?}

\textit{Oh my god.}

No one has ever been able to silenced Qing so severely, so it could be said that this was a historic feat against the master of the Hell's Formless Poison.

Qing took a deep breath.

\textit{This guy seems to be talking nonsense these days.}

Qing disappeared out of the room.

Then, she came out of the door, groaned, bent down with a heavy sigh, and then returned, dragging something from behind the door.

A man was being dragged helplessly, his hair held in her hands, a very thick, bloody tail drawn on the floor, almost like writing large letters in blood.

Daeyoungban shouted.

``Jang Cheon-ho! You bitch, can you not let go of that hand?''

So that's what Qing did.

Thud! His head hit the floor with a loud thud as the hair she's holding was released.

``You bastard, how dare you! Jang Cheon-ho! Come to your senses!''

``……! ………!''

There was only the sound of the wind blowing back.

The reason why Qing's specialty, making a hole in the windpipe and turning it into a whistle, was so effective was because it made low noise.

They say it's this quiet if you opened one breathing hole.

She put her hand on her waist.

"See? You think I'm easygoing, but I've already captured your subordinate. I'm actuall a scary person, you know?"

\vfill
\begin{lstlisting}
	The chapter title is a reference to 'Great Teacher Onizuka'.
\end{lstlisting}