\chapter{Great Instructor Ximen Qing (15)}

The Blood Cult Trio, the so-called Three Idiots, lost the bribe they were counting on last night during a close encounter with a minor witch.

This bribe, this elixir of solitude, was not only a mission given to them by the Blood Cult, but also the key to ensuring their future successful infiltration into the Wulin Alliance.

The Jeongpa bastards will definitely pay for their bribes. If you give one each to the head of the academy, the administrative officer, and the direct instructor, they will definitely join the middle combat unit of the Wulin Alliance.

So, there was no need to pretend to be friendly with the common officials who had no ability, no background, and even less the means to prepare bribes.

But the key was taken away.

This would change the situation.

Besides, if Mahou was to point out that even the White Hand Witches were pathetic people who had lost the favor of the people in the academy, doesn't that mean that there were more petty kids burning with ugly jealousy than you might think?

So what?

``Hmm? You? Aren’t you supposed to be cleaning?''

The officials who returned from washing up were confused.

Because I saw the dormitory floor, which was so clean it was almost shiny, and Jo Hyun-il holding a mop in the corner.

"Oh, guys. Just, to clear my head. I've been a bit sensitive lately due to some unfortunate events…"

You might ask what kind of trick this is, but from the men's perspective, it was a very impressive scene.

Because men don't say sorry so casually.

So, a man's apology should not be a pathetic excuse like "I'm sorry" that needs to be immediately addressed, but rather it should be done by quietly bending down and speaking first.

It was a bold and manly way of acting, not just talking.

For example, after a big fight, when things were still cold, they often express their regret and willingness to reconcile by saying things like, "Aren't you hungry?", "I'm craving a drink, come out", or "Want to have a cold drink?"

The officials looked at each other and-

``Oh, brother Joe, there’s a set order, so why bother writing like that? Who was it today, brother Oh? You were the only one playing.''

"Why was this guy doing this? He probably hasn't even washed yet. Hurry up and wash up."

It was the law of men to pretend nothing happened, to accept it as if nothing had happened between us… …!

In other words, it was a dramatic moment of reconciliation between men.

``But it’s not a good thing, were you okay?''

``Yes, well, it worked out well…….''

"Yeah, I'm glad it went well. Okay, go wash up quickly."

As Jo Hyun-il stumbles out, the officials look at each other again.

``I told you, that guy was a good guy.''

``I thought the kid was acting a little strange lately, but then something happened. It’s a relief that he’s come to his senses now.''

This was also a characteristic of men.

I don't know why he's acting like this, but he's being criticized in front of me and praised behind my back, so I guess it's not his true feelings.

"But what happened? Even if it was personal, you were staying at the school anyway, so you didn't receive any letters, did you?"

``Yeah. People suddenly change. Hmm?''

Now that I think about it, wasn't there already a guy who suddenly changed before?

``Come to think of it, didn’t you get advice from Instructor Ximen?''

``Ah, I see, that’s what happened.''

"As expected, it's Instructor Ximen. Of course, I couldn't continue to act so arrogantly after hearing those precious words."

Normalization was the effect of the counseling provided by the Ximen instructor, who makes your heart swell after listening and presents a secret vision for the future.

"I still can't forget what Instructor Ximen said. He said, 'Youth was all about pain.' Wow. How good!"

The pain that doesn't kill you was just a hammer blow that makes you stronger.

A stone on the roadside may be broken by being struck, but the steel that has endured the pressure of the mountains and the mineral veins of the deep earth becomes stronger through being struck, and was finally born as a famous sword.

Will you live as a common stone, crumbling from pain and turning into a grain of sand, or will you become steel that has silently endured the pressure of a mountain, forging yourself into a sword that transforms suffering into achievement?

How will you live!

"Wow, as expected, a swordsman must be reborn with a single sword. This was not the time for me. As the instructor said, one swordsmanship makes ten thousand. Is there anyone who can cross swords with me?"

``Oh, this guy’s going ahead on his own. Should I come with him?''

``Brother Yoo, were you trying to leave out my younger brother?''

Anyone from the Qing Dynasty would say, "Are you saying something that sounds familiar, something so obvious that it's almost annoying."

This was the central plains.

It's still hundreds of years away from the emergence of extreme sales tactics in the Zhongyuan that were written as self-development (development? new foot?) and read as success sales. So, aren't they truly the elites from the future?

In fact, success marketing was a despicable fraudulent act carried out for the purpose of making money, boasting, or both.

However, there was a positive side to this scam. After listening to it, you somehow felt like you had become a better person, and your motivation rose for a short time (depending on the person)!

And Qing was a young master who has reached the pinnacle of skill at a young age of only twenty-two this year.

He was a master who dares to be called the next best in the world, and one could even say that he has already achieved success.

What would be the power of future propaganda coming from such a mouth?

Because it was a speech that was fatally effective for people in the middle class who were not yet immune to self-development.

``I become a master. I become a master. I become a master. I become a master.''

``Hmm? Oh, what were you mumbling about?''

"Ah. This was the communication that moves the energy of the universe through thought. This was the method of attraction that Instructor Ximen taught us…"

What was the foundation of martial arts, Chukgi?

It was to hold and gather the energy of the universe with one's breath. This was how humans communicate with the universe. Just as I move my own energy, the energy of the universe and nature also waits to respond to humans.

So seek, believe, and act.

This was the secret of the masters, 'that secret'.

In fact, as a cultured person from Qingdo, I wondered if it would be okay to talk about such pseudoscience, but it seems like the topic would be more suitable for the Zhongyuan than my hometown.

But still, this place was really cool, right?

I wonder if Oh Gwan-do, who has low self-esteem, needs the power of self-affirmation.

Although it prickles my conscience a little to speak of the contents of a book written by a successful future arm as if I had said them myself.

But in the first place, isn't a self-development book just a mother's nagging expressed in fancy words?

Be positive about yourself and the universe will help you.

This was telling you not to give up.

Morning was important, study in the morning.

Study when others were resting, you have to study during your rest time.

Night was important too, work hard at night too.

I wake up all day and study, eat breakfast, study, eat lunch, study, eat dinner, study, then sleep, wake up, and study in the morning.

You should do it in your teens. You should do it in your twenties. Your thirties were your golden years. Don't miss your forties. You should do it in your fifties, too. Studying was a lifelong pursuit.

It means to work so hard for your goal.

If you don't rest and work hard, you will succeed. How can you not succeed?

Is there anyone who doesn't know this?

Just filter out the self-help books that use terms they made up, like developing the brain, changing consciousness, and establishing a computational method for handling work, and brag about how they've already succeeded and say things like, "The author decided to call this process 'dream-like'."

As Qing plagiarized the contents of future self-development books and spoke eloquently, the officials' motivation skyrocketed.

According to one author who said that 10,000 hours was something, we need to create an environment where sustainable efforts can work rather than hard work.

From the transformation into Wan Talu, to the three idiots who were boasting about having reached a certain level, to the 'counseling' of the Heavenly Blossom Sword that even influenced them.

Everyone shines with passion after three rounds of motivation.

Since everyone was like this, a virtuous cycle was created in which everyone looks at each other and strengthens their will to continue practicing.

If it were a medium or film in the homeland of Qing, it would be the starting point of a production that connects scenes with moments of effort along with very hopeful and cheerful music.

The days of the academy flow like a painting, or rather, like a scene from a movie.

It was a sweaty summer… …

The concerns of the officials who came to Qing for advice were almost all resolved by plagiarizing self-help books.

Actually, it's hard. I don't know what training was or what a sword is. I wonder if I'm doing well. I don't feel like I'm growing at all.

Then, you'd say, "You're doing great," and then, "Just try, just try." Everyone would be impressed and motivated, and they'd rush out, ready to swing their swords right away.

However, not all consultations were like that.

``Instructor. That instructor, um, no, no. Excuse me.''

"If you have any difficulties, please feel free to talk about them. Even if you don't find an answer, you'll feel better. This instructor was very tight-lipped."

"Ugh, that's what I mean. Ugh, Instructor Ximen was beautiful, so I guess she understands men's minds well. No, that's not what I meant, but I think a lot of men would follow her…"

His blue eyes sparkled.

Isn't this relationship counseling?

Anyway, Yeo Gwan-do, Yeo Ju-il Gwan-do, was one of the two women who followed the Blue Dragon Dancer around, so this was definitely love advice.

Would Qing miss out on this fun event?

"Haha. Official. This instructor was already no different from a man, no, he's a man himself. Let me speak quickly."

``Well, I, I don’t really know these days.''

Yeoju-il, who had been hesitating, confesses her worries.

Although he has been in love with the Blue Dragon dancer Chae Seong-ha for a long time, he still wonders if he even sees her as a woman.

He clearly saved her from bandits, and also from a political marriage within the family by revealing that her fiancé was actually a hypocrite and a scoundrel.

However, as a result, Chae Seong-ha told Yeo Ju-il, who had suffered the dishonor of a broken engagement, that he would unconditionally side with Yeo So-jeo and that he would believe in her and support her even if the whole world pointed fingers at her.

Qing was honestly a little impressed.

Well, this kid. He really screwed me over.

With this level of fate, aren't they already a couple?

If it's come to this, can't we already consider it a common-law relationship?

But that admiration was short-lived.

"But these days, I don't even know if they see me as a woman. Chae So-hyeop just tries to save anyone in trouble, so I thought, 'I'm in trouble, so I helped.' I wonder if I'm the only one who harbors such feelings, such affection."

Moreover, nine out of ten of those in trouble were women.

Even just the second follower of Chae Seong-ha, Lady Jeong Sil-im, who had been bedridden since birth due to a chronic illness, was revived by giving her an elixir, and many other women also benefited from her grace. So, even if they could not follow in the footsteps of Yeo Ju-il and Jeong Sil-im, there were already about five women who bowed deeply and said they would wait their whole lives.

``But these days, I’ve been hanging around with Lady Chang, and I don’t know if she’s reading any signs of trouble, but whenever she gets the chance, she tries to talk to me, and I see her, haaah…''

"That's a really cruel guy. Oh my goodness, saving me was all you need? If you take my heart, you have to take responsibility, you son of a bitch."

"Don't say that! Master Chae was simply too delicate-hearted, blind to the plight of others. And it just so happens that it's women's plight…"

Hmm. Empathy failed.

It's surprisingly picky…

"Well, he mostly saves women from trouble, but he doesn't do it on purpose. He's just oblivious and indifferent, and he's never really interested in women in the first place, so he doesn't recognize their affection. Is that what you're saying?"

``Yes, so, how can I capture the heart of Confucius Chae? Wouldn’t Instructor Ximen be able to help me……''

``Hmm.''

Hearing this, isn't he just a guy who's into picking up women? If he's carrying around two women and then flirting with other women, he seems like a total hooligan.

But don't give up, the way I see it, he's just a loser. Whether he's a rascal or not, he's a loser. How can you possibly have a proper relationship if you cling to such an oblivious and indifferent guy? You can't say that, can you?

Listening to what you say, it doesn't seem like it will work.

"Well, have you ever personally conveyed your precious feelings to the female officer? If you're so tactless, you probably should have."

"Well, I once mustered up the courage, and just as I was shouting, 'I love you,' the building next to me suddenly collapsed. Some kind of civil engineering goddess? Some strange priestess? They were causing a ruckus. Thanks to that, the Master threw himself at me and hugged me tightly, but how strong, oh my, hehe…"

Qing was sweating profusely. What was this, Civil Engineering Goddess, suddenly barging in like this?