\chapter{Great Instructor Ximen Qing (6)}

A group of martial artists climbs the mountain.

If anyone had seen it, it would have been a very strange sight.

First of all, the sight of a man carrying a corpse that has fallen to the ground, his back bent in the opposite direction, his legs, arms, and head all swaying and shaking without strength, makes it obvious to anyone that he was carrying the body of a precious person.

Despite this, the group's expressions were bright, and they keep smiling at the corpse.

Perhaps you could be solemn and think of it as a solemn scene, a cheerful farewell to a colleague who had already left.

It's just the return of the Blue House to the Blue House, and the Blue House was just hanging on.

If the trunk was bent due to damage to the organ, it hurts.

He was held in Murong Zhuji's arms and tried to change his position here and there, but eventually he found stability by relaxing and slumping down.

Hmm. I miss Yi-mei. Yi-mei was more comfortable.

And your hands won't be bored either. Murong's lower body was amazing, but, um, it's hard. Wow, was that all muscle?

Even if Murong Zhuji beat Qing, he was innocent.

From the position of someone who was carrying someone, and not even on flat ground, but on a mountain, isn't it a situation where, even if it's not difficult with the highest level of skill, isn't it extremely uncomfortable?

In the meantime, she was touched by a bad hand that groped her back, buttocks, and thighs, so even Murong Zhuji could only protest softly with her earlobes red.

``Uh, ma’am? If you do this, then this was fine, but, uh, when it’s just the two of us……''

"Oh, I don't know. I guess I just reach for it because there's something there. You know what I mean? Hmm?"

Wasn't that a protest? I thought I heard something really snarky. The moment Qing's eyes narrowed,

``And forty-two, then aim for the little witch’s heart with the Tathagata Goddess, the Thousand Flower Sword? Are you listening?''

``Oh, was it really necessary to go into such detailed settings?''

``Oh, oh, oh. Thousand Flower Sword.''

Since Qing kept shouting 'I am a witch' with her own mouth, the excuse of being a goddess or a divine beast became useless.

But since we can't hide Qing's injury, it's better to separate the two.

While Heavenly Blossom Sword was chasing the assassin, he suddenly got into a three-way fight with a witch who had suddenly appeared.

In the process, the assassins were all annihilated, the Heavenly Blossom Sword was injured, and the minority witch was also injured and fled.

It was good up to that point.

I nodded and said, "As expected, smart kids can make up stories in no time."

But why were you so obsessed with details?

They've been talking nonstop from the first day to the forty-second, so it's quite exciting and fun to listen to, but, um, do you want me to memorize it all?

"You're incredibly complacent, aren't you? As pioneers of our time, our brilliant reputations were always followed by dark shadows, envy, and jealousy. If these people were to question us in disbelief, wouldn't we exaggerate even the slightest discrepancy and call it a lie?"

The saying, "a small needle was like a big club" means to blow up something small and make a big fuss about it.

The virtual life and death match between the Heavenly Blossom Sword and the Soso Witch must be firmly woven and engraved in one's mind.

Otherwise, there will inevitably be some inconsistencies, and those who do not want to believe it in the first place will obviously claim that it was false just because of this.

That makes sense, though.

I knew there were idiots like flat-earthers in my hometown of Qingdo, who rejected hundreds of thousands of scientific evidence and called it a lie by finding fault with one or two things.

But anyway, it's not that I don't trust these kids, it's that I don't trust them, so I can just ignore them. And even if they fought in the first place, wouldn't it be strange for them to remember every single detail?

But it's fun, so let's listen to it some more.

Thus, the magnificent battle between the Heavenly Sword and the Little Witch unfolds through Sima Chunfeng's mouth.

A truly heaven-shaking, earth-shattering, heart-pounding showdown!

Friendship blossoms among friends!

In particular, the command tower stands out, and the performance of Jinang Hyeonhwa Sima-lang, who maintains composure even in the midst of an urgent battle, and who powerfully commands the witches by understanding their habits and weaknesses…

And finally, at the end of this life-or-death battle that will be remembered in history, the witch Sosu was pierced by the gutsy blow of Sima Chunfeng, who was half-dead.

What? Didn't the main character subtly change?

And wasn't the setting that the minority witch was badly injured and escaped? If her heart was pierced, she escaped, or was it a story that she escaped from this world to the afterlife?

But it was definitely fun.

Now that I think about it, Chunfeng would have been a very successful comedian.

If we assume that Chunfeng was a witty person who tells stories, then honestly, it would be fun to just look at the area between his face and his stomach rather than the story, and I think I could watch it endlessly.

Of course, it would be a bit strange to beat up the Wulin Alliance military and then become a shaman.

What if it's not a matter of self-realization?

The story unfolds as a witch, her heart pierced, goes berserk and transforms into a pitch-black monster. Ah, so that's how it was meant to be. Chunfeng had a plan.

He quietly looks at Sima Chunfeng, who was spitting out words with his head turned upside down and his chin pointed to the sky.

``And this Sima-lang, the first of the Ten Sects of the Sword, the sword of creation… um, the Heavenly Flower Sword? Why do you look at this Sima-lang like that?''

"No. Actually, I thought you'd tell Alliance first. You even went so far as to make this story. Well, it's a little late, but thank you for your consideration."

In fact, my friends have already seen it for a long time, and even if I were to blow up not just the minority magicians but the entire group of the Heavenly Demon Gods and the Ten Greatest Magicians of the World, they would all pretend not to see it and just ignore it.

But isn't Chunfeng not at that level yet?

Of course, just looking at him, it seems like he doesn't have any friends, and I seem to be the only person he can call a friend.

Still, I'm grateful.

Gratitude can only be expressed through words.

``No, Heavenly Blossom Sword, that, again.''

Sima Chunfeng's face turns red.

``Of course, it’s something that needs to be reported to the Alliance and countermeasures established, but I, ahem, people like us were jealous, we’re making mistakes, that is, throwing ourselves into a fireball. In my judgment, a Heavenly Blossom Sword with such noble intentions wouldn’t be able to rashly create a mistake, something like that…''

Qing's graceful eyebrows slightly arched in the opposite direction.

On the contrary, the corners of the mouth slightly rise.

It was a self-deprecating smile, as if embarrassed, as if as if he were ashamed, as if he were sad.

Of course, that's true.

How much of a hero would he look like if he threw his body away to protect the civilians and blocked the fireball?

Anyone who hears it will know that it was a good thing and a righteous thing.

Well, that's what I wanted to look like.

A monster that doesn't listen to poison and has iron fragments embedded in its body without any damage.

A thief who learned all kinds of new techniques by stealing them.

Even if he had collected more than half of the ten greatest magicians in the world and was ready to learn them all if necessary, he would be caught by the great magician who had been holding onto his skills through trade just in case.

If these things pile up, I think I might be able to be forgiven, thinking, "Well, if you look at what I've done and what I've done, I guess I'm a good guy."

Because I want to receive it.

Qing tries hard to cheer up her sagging mood.

"Come to think of it, you and Sima-lang have never slept together, have you? True friendship should be like that. As soon as you get better, you should sleep together right away."

"Huh…? Are you talking about a friendship where you share a bed? I guess that doesn't mean you actually share a bed—"

"Hey, that's just because friendship doesn't measure up. Does saying you wouldn't sell something even for a million gold coins really mean you wouldn't sell it even for a million gold coins? Who wouldn't sell something for a million gold coins? In other words, you can only truly declare, "I wouldn't sell it even for a million gold coins," after you've actually put it into practice. Only then can you truly say, "I wouldn't sell it for a million gold coins."

``Why all of a sudden, a million gold coins…?''

"It's the same with beds. They say they're close enough to share a bed, but since they haven't actually shared a bed, they're speaking in terms of assumptions. In other words, it's a friendship where you don't share a bed, but you could share a bed if the occasion calls for it? But once you share a bed, you're actually sharing a bed. That's the level of friendship. Right? A deeper friendship than a friendship that shares a bed was a friendship that already shares a bed. Right?"

``Huh? Really? Uh, that makes sense……?''

Then, swoosh.

There was one shadow blocking the way between the two.

Xue Iri's expressionless face as she walks forward, pretending not to notice.

I'm angry, so I won't hang out with you. I won't talk to you, and if you do, I'll ignore you, and I won't do anything you ask me to do. Anyway, I'm angry, I'm upset.

But I will always be by your side.

Well, Gunyeong isn't some kind of cat, and he gets really annoying when he pouts…

The return was a day, exactly half a day, later than the original two-day, three-day outing schedule.

One day I was drinking and messing around, another day I had fun with captured assassins, today I'm eating breakfast and climbing a mountain.

From Qing's perspective, the day was empty.

Well, that's because I lay there all day, completely unconscious. I lost an entire day.

It's not even late alone.

He brought along a bunch of assistants, and even took out someone else's assistant, Pang Dae-san, and was late (of course, Pang Cho-ryeo was very happy. Could this kid really be? Finally?). As an instructor, it was a mistake that he couldn't explain even if he had ten mouths.

So, first, let's kneel down in front of the governor as a group.

Since the admissions office had already informed me through messenger that there was a commotion, there was no particular reprimand.

"I heard the story. There was chaos, right? So, what exactly was the chaos?"

Then, from Qing's mouth, a tense scene from the past unfolds, a battle that makes your heart race.

Assassins targeting the official route! A small number of witches have intruded!

And then, from the middle part of the story, the main characters suddenly change and it becomes a desperate life-or-death battle between Sima Chunfeng and his party!

Yu Shan-ye, the head of the Department of State Affairs, rubbed his forehead.

``That… Phew, no. Chunfeng, you stay and see me later.''

It didn't work.

Even so, the reason why Qing brought up Sima Chunfeng's creative fight story was because, since it was so absurd, it would be better to say something completely absurd.

"But, the Golden Guard? You're targeting the Tongjeongsa's son? Huh? Following the Sichuan incident, you're acting so fiercely in the palace. This was serious."

``Master Yu, you have to hear this Sima-lang-''

"That's something the Military Department will discuss. Don't talk carelessly."

At that, Sima Chunfeng's lips stick out in a pout.

Sword-dominating Dagger Yu Shan-ye was the commander-in-chief of the Wulin Alliance and the person in charge of the administration of the Wulin Alliance, so he could not help but be close to the Military Department personnel in charge of the details of the administration.

So, it was natural that his friend's daughter was comfortable with him, and that was why he was particularly picky with Sima Chunfeng.

Leaving the aftermath to Sima Chunfeng, it was now time to return to the school schedule.

Before that, let's eat lunch. Lunch.

Um, soup again, I don't like soup…

Since rice was boiled in plain water, it obviously wouldn't have a plain taste or flavor.

Qing's shoulders slump.

I want to argue that I can eat rice, that I can eat a lot of greasy, heavily seasoned, and spicy food.

What can I do when my friends were unanimously and unanimously opposed? I'll sneak out and search the restaurant later tonight. I've already searched all the restaurants.

And only then does Qing appear on the swordsman's platform.

"I apologize. This Instructor is temporarily unable to move due to an injury. I will provide guidance in the form of an observer, but I apologize for not being able to fulfill my duties as an instructor."

Since those who had gone out had already returned, rumors about the chaos in Nosan County were rife, with no definitive answer.

A group of assassins ran riot out of nowhere, and a small group of witches appeared out of nowhere.

And the instructor who hadn't been seen all morning was injured, so it's not surprising that Moyara was involved in that.

I'm just a bit curious.

Amidst everyone's curiosity, the academic schedule of the Yizheng Martial Study Hall resumed.