\chapter{Great Instructor Ximen Qing (17)}

Sima Chunfeng enters the room with awkward, stiff movements that make him feel awkward.

``Oh, Sima-lang, you’re here. Did you have a good trip? Did everything go smoothly?''

"Of course, the land of Hanam was the front yard of our Taemurim Alliance. As the youngest deputy military officer, I, Sima-lang, effectively control this territory. It's a place where no untoward incident can occur. So, while I, Sima-lang, was away, nothing happened at the academy, right?"

``Yeah. Nothing really special, but there was a spy from the Blood Cult in the school.''

``Haha, well, it’s common for a traitor to sneak into any group, right? Blood Cult, yes?''

Sima Chunfeng, who had been smiling and agreeing with the story of seeing a strange beggar on the street, suddenly feels a great sense of unease.

``Wait a minute, Blood Cult? Are you saying that the evil servants of the Blood Cult have infiltrated our political and martial arts academy?''

"Yeah. That's why I'm worried. I can't handle this quietly, but I can't bring it up openly either. Thinking about it alone won't lead to any conclusions, so I need to ask someone smart."

Even though winning the Blood Cult prize meant we couldn't have a good time, it was thrilling to think about it, but what would happen to the reputation of the Yijeongmuhak Hall if three of its officials went missing?

But I couldn't reveal it, so I held such a grand entrance exam, and then it turned out that there was a spy from the Blood Cult. It would be a shame to do that.

What if that happens?

There may be some who believe it, but if they don't, wouldn't there be potential for various problems, such as the issue of dealing with problematic officials by pushing them into the blood cult?

To consult with someone, let's make an exception for San or Zhuge, who were diligent in other subjects.

If it were a blood sect, Lady Murong would roll her eyes.

Gunyeong deserves praise just for being able to breathe, so what kind of counseling was that?

So, I had no choice but to ask Sima Chunfeng, a smart man who was part of the Wulin Alliance Military Department and could report directly to the management.

They're not the kind of guys who'd run away if you left them alone anyway, and they're parasitic lizard addicts that can be neutralized with an ultrasonic attack from a bottle of alcohol, so there's no need to rush, right?

``No, how, was there any evidence, was there any evidence?''

``I pretended to be a witch and it was easy to speak.''

"ah."

Sima Chunfeng was immediately convinced.

The White Hand Witches would have no choice but to serve the leader of the Blood Cult as their superior, even if the Blood Cult was divided into several factions.

``Um. For now-''

``Oh, we’ll talk about that later. Just a moment. The kids were coming.''

The Blue's hearing picks up a series of sounds approaching the room.

In fact, even without hearing, it was time to come, and with a knock, the faces of familiar friends were seen beyond the door that opened naturally without knocking.

Ciyu, who had come running, went around behind Qing-ui and hung on, putting her arms around her neck.

Since Qing couldn't hug her due to an injury, he offered to hug her himself, but it was more like strangling her than hugging her.

Of course, the muscles of the neck were eternal muscles, and so were the muscles of the neck, so no matter how hard you try with just the strength of a woman, it will only end up being a little frustrating.

"who?"

``It’s been a good day with Sima-lang today.''

"oh."

His eyes sparkled with joy.

I couldn't take my eyes off that towering, rugged pocket of wisdom, because lately my pillow had been too low, making my sleep unsatisfactory.

``Are you Sima-lang’s mom too? Are you sleeping with me tonight?''

``Hmm. Would it be difficult to be a mother? What do you think, Sima-lang? Do you want to be a mother too?''

``Huh? Suddenly? What were you talking about, Sima-langdo, Dorani?''

"The more mothers, the better, right? With Murong, Iri, and Jang Myeong, not just anyone gets the honor of being my daughter's mother, right? Right, Ziya?"

``Yeah. Yeah.''

Ciyu nodded, resting her chin on Qing's shoulder.

``No, what kind of- No, no.''

Sima Chunfeng was about to ask what kind of nonsense that was, but a thought suddenly occurred to him and he quickly brushed it off.

"You said he was a child rescued from the evil sect of the Blood Cult? Furthermore, Heavenly Blossom Sword was still young and unmarried. If he can't be raised in a normal family, it would be better to make his parental absence a minor matter. Yes, for example, having multiple mothers."

Besides, this was not a particular flaw for women who call themselves mothers, so it would rather be praised for their kindness.

Indeed, Heavenly Blossom Sword, this was a wise action worthy of the close friend of Sima Rang.

Although the person was strange, it was definitely the head of Sima Chunfeng who was clear-headed.

It immediately sees through Qing's intentions.

And Sima Chunfeng was a strange person and his way of thinking was very much like the consciousness of the chosen people, but he was a good person whose karma was quite extraordinary.

"Huh, that's right. So you want to be the daughter of the famous Sima-lang? That's probably the wish of every child in the Zhongyuan, but hehe, that's fine. You'll be honored."

"oh."

With a few simple words, Ciyu runs over and hugs her new mother.

It's not a particularly moving sight, though, as it's been crushed and buried in something.

Still, isn't it a blessing that he readily accepted? He's a good boy. He's a good boy.

Well then, let's leave the recent news at that.

``Okay, then, let’s begin.''

Qing claps, calls attention, and immediately pulls down her clothes. The clothes crumble away like ice rolling on an ice rink.

``What, what, what, what……! Heavenly Blossom Sword, what was this? Why, why were you taking off your clothes?''

"Huh? Treatment. We need to remove the fragments."

The group, already experts at extracting fragments, tapped the tongs without much interest.

And then, expressionlessly and familiarly, he groped the naked body, then stabbed it with the tongs and grabbed the fragment protruding from the skin, Ouch, ugh, owah.

It was a bizarre scene that I could not see anywhere else, a scene that I was afraid I would see again, like birds pecking at a corpse, a scene that made me wonder if the wind in the west was like this.

Is this the right treatment?

But the sound of the fragments falling from the iron sledgehammer, looking back now, I see countless scars on Qing's skin, long and short scratches that have not yet healed.

Sima Chunfeng gulped at him.

Sima Chunfeng was once again reminded of what it meant to block Jincheonroe with one's body and how disastrous the results would be.

I thought it must be okay since Qing was walking around well, laughing well, and talking well, but how could that be? Even after hearing that countless pieces were embedded, it didn't really feel real.

"No, how foolish. Don't you realize that the body of the Heavenly Blossom Sword, the Heavenly Blossom Sword, doesn't belong to the Heavenly Blossom Sword alone? As the leader of our era, destined to lead the future of the martial arts world, such a weighty responsibility rests on your shoulders. How could you be so reckless? What foolish behavior on earth…"

``Oh, suddenly I feel like I’m being scolded, ugh.''

Chen Changming nodded as he pulled out a fairly large piece.

``You deserve to get scolded. No, you deserve to get scolded a lot.''

"that's right."

Even Murong Zhuji interfered, and even Xue Iri, who had her eyebrows slightly furrowed, turned her head away without expression.

``Don’t you understand? Didn’t a former general ask his teacher to teach him, saying, ‘Even if you hone your martial arts, you can only face a hundred men. However, if you learn the art of war and lead your troops, you can face ten thousand men (만인지적萬人之敵)? This was the principle of a general not taking the lead. Even if you display your bravery in front, the result was only a hundred men. If you sit high and command, you can destroy the enemy’s country. How can Heavenly Blossom Sword, with such great talent, treat his body so carelessly with such shallow thoughts? This was also unfilial piety, injustice, and cruelty. Indeed…''

It was a frustrating nagging that kept popping up.

Well, this kind of atmosphere was a bit uncomfortable… … .

But what can you do?

This was a disaster and a consequence that you brought upon yourself. In the end, you will reap the consequences of your own actions. This was your own karma that you must bear.

After today's treatment, which felt unusually long, was over, Sima Chunfeng laid out the Wulin Alliance's response to the recent Gaepyeongdagu attack.

First of all, since the people gathered here were also the parties involved in the commotion, it was something that had to be conveyed in order to reach an agreement.

"For now, we've decided to announce that this was a fight between a group of hired assassins who harbored a grudge against a White Hand Witch. In other words, the assassins weren't targeting the Wan Talu Pass, but rather the White Hand Witches themselves. You all understand what I mean, don't you?"

As he said this, Sima-lang looked around the room and covered his mouth with a ``Oh, no.''

"Ah, my dear, this was the mistake that I, the Bone Sima-lang, would have made. If I, the Heavenly Flower Sword, were worthy of daring to compare with the world's most talented women, I wouldn't understand it, but you, mere ordinary Geomhwa and Binghwa, don't? Oh, truly, the sorrow of our prophets, of geniuses, who must advance and await the foolish. That's what Bone Sima-lang meant…"

As Murong Zhuji and Xue Iri, who had suddenly become ordinary people, had their tendons sticking out on their foreheads, Sima Chunfeng began to explain.

In fact, it can't be helped that it's a really dirty situation.

Just because the royal family was blatantly plotting something, what can the Wulin Alliance do?

Could the Wulin Alliance express any regret to the royal family, or even protest?

If it were the hometown of Qing, then any such act would be considered treason in the Zhongyuan.

Because the Emperor was the father of all people and also the master of their life and death.

In a world where one must die when the emperor orders one to, how can an object that was owned dare to harm its owner?

Of course, that was the law of the land and the country's governing ideology.

Since the Zhongyuan have been dominated by power since ancient times, they developed justifications to keep this in check.

No matter how much of a king he was, if he lost his legitimacy, the consequences would be bad. So, isn't the reason why heroes rose up and established a new dynasty to provide a legitimacy that could replace the existing emperor?

The shackles that prevent those with power from wielding their power as they please were called a just cause, and so they were called a just cause.

Even if he was the emperor, if he continues to commit tyranny without justification, won't it not soon be overrun by bandits wearing dyed hairbands and wielding swords?

The incident with Sichuan the other day was also like this, and the reason for the secret dirty tricks being done in the palace was precisely because of this excuse.

So, the official announcement of the Wulin Alliance was also a means to avoid giving this excuse.

"The instructors of the Euijeong Martial Arts Academy confronted the White Hand Witches, but were ultimately defeated. However, countless righteous warriors sacrificed themselves before them in their quest to punish the evil of the Blood Cult, and the Wulin Alliance will never forget their courage. To prevent such an incident from happening again, the entire martial arts world will unite to prevent it."

If someone who doesn't know hears it, they might think, "Oh, I guess so."

If we assume that the Wulin Alliance knows the assassin's purpose and identity, then the interpretation of this announcement would be as follows.

It was truly unfortunate, but all the assassins sent by the Emperor ended up dead.

We didn't kill them, the White Hand Witches did, so it's not our fault.

Well, anyway, we will never forget this.

And if something like this happens in the future, the entire martial arts world will join forces and rise up, so unless we really want to settle things, let's stop now.

A brilliant move that completely blocks the imperial family's intervention, while also conveying Meng's position as a threat: "If we all rise up, can you handle it?"

By the way, the military department didn't know that they would live to be grateful to the witch of the Blood Cult.

I don't know why the White Hand Witch was there out of nowhere, but thanks to her, the burden on the Wulin Alliance has been greatly reduced, so wouldn't the public enemy Blood Cult excuse be the best excuse without any repercussions?

Sima Chunfeng, who knew the identity of the White Hand Witch, just smiled meaningfully and received the glares of the soldiers who thought that was very suspicious, but Sima Chunfeng thought that receiving glares was normal and that the jealousy of ordinary people was natural.

``Hmm, I wonder if it’ll be okay……''

Qing trailed off.

That's true, but I think it's too much.

Qing had actually experienced military bombardment, so after entering the harmony, he could just use his lightness to escape, but why would he be afraid of having difficulty protecting himself?

What about those guys who can't even sew, those unmanned appealers who were below the peak of their power? Those lumps of blood who can't even walk, who crawl around.

If you think you're falling for our priestess's gate, oh well.

"But I can't just take it forever, can I? If I don't properly express my intentions at least once, even if I fall for these tricks just once, it could be a disaster."

That too, though.

Wasn't he the emperor who tried to gain legitimacy by killing his own younger brother in Sichuan back then, and this time, wasn't he trying to gain legitimacy by killing the eldest son of his favorite?

It was an action that could not be considered sane at all, so if that guy gets really angry.

Of course, that doesn't mean we can just turn a blind eye and pretend not to know while they continue to slander us.

Qing rolls her head for a moment, then shakes it off.

Well, it was decided by the military department of the Wulin Alliance, but if the smartest people in the Wulin Alliance had gathered together and decided, then what a foolish thing to do.