\chapter{Great Instructor Ximen Qing (10)}

When I woke up in the morning and lifted the cotton cloth covering the affected area, I saw that a scab had formed overnight and the area was swollen and swollen.

But even putting aside the small ones, the big one was a wound with a piece of metal the size of a finger joint stuck in it. Is this correct?

Of course, it was also thanks to the fact that the golden elixir was a good product to begin with.

The golden elixir that Qing carried was either a special product of the Tang family or an imported product from the Seolga Trading Company (a secret of the Demonic Sect named after it).

Its efficacy was truly the essence of Oriental medicine!

Even in the Zhongyuan, it was a world where the mysterious energy of the universe exists and even dwells in plants, enhancing their medicinal properties.

If such a miracle drug meets a body with superhuman, three times faster recovery, this was what it's like.

Of course, the pieces that were still deeply embedded will take some time to come out, and this process will have to be repeated every night.

Well, it's good if it's sturdy.

And I'm glad I kept my heart, really.

He lay face down, holding Jincheon-roe in his arms, his hands clasped together and clasped to his forehead. His forearms were anything but ordinary. They were the indestructible, diamond-like arms of a sousu magician, unblemished and unscathed.

Of course, the weight of Qing's chest was not enough to cover it to that extent, but since she was lying on the ground, the overflowing part was crushed, and thanks to its softness, she was able to remain unharmed.

I guess it wasn't.

It almost became a rag.

Of course, this heavy lump of flesh was just uselessly uncomfortable, and when I touch it, I don't feel anything special, it's just useless trash.

But, cutting it off like a rag… well, it hurts. It shouldn't hurt. Okay. Well then.

And even if you sleep, you won't be sad.

When Qing turned his head, his eyes met with two rotten eyes that were staring blankly in that direction.

My daughter, Ciyu, always looks tired because of the dark circles under her eyes.

``Why aren’t you sleeping? Why aren’t you sleeping?''

A smile spreads across the child's face.

However, because the impression was so rotten, it ended up being a very tired smile.

And then one word.

``It’s uncomfortable.''

``Are you uncomfortable? What was it?''

``It’s hard.''

Why did I look so dissatisfied from the morning? I guess it was because the pillow I was lying on was too low and hard.

"This was already covering up your nipples? Come on, Seol's mom should be satisfied. Do you want to sleep with Mo-yong's mom?"

Gunyeongi was a relatively small, compact device that fits in one hand, and it's also refreshing. And it doesn't break.

I feel sorry for Lady Mo, but for Ziyue to lie down, it's just like putting a blanket on a stone bed.

Kihihihi, the sound of Ciyu giggling.

And then, gasp, the sound of someone gasping for breath.

Oops. Qing turns her head to the other side.

His large, tearful eyes looked at Qing, and he let out a sad, groaning sound.

"Hmm. Miss Murong. Did you sleep well? Wow, good morning, refreshing morning. Wow, I feel light. Do you feel the same, Miss Murong?"

``My lady, what do you mean……''

Miss, they say you have a sweet mouth.

Because I was so careless after waking up, I didn't pay attention to Lady Murong's breathing.

Well, who on earth wakes up in their room and immediately looks around?

``You said I should be satisfied with something like Miss Seol, but I’m too small. Is that so, was that so?''

"Um, that's not it. Oh, right. It's cool here. You know what? The North Sea people keep betting even while they sleep. They keep emitting cold air throughout the night, so the room was cool right now. Isn't that amazing?"

``You clearly said that Ciyu would cover her nipples… because mine was too small, right?''

Turn the tables, fail.

Perhaps because his sensitive parts had burst after a long time, or perhaps because his head was small, his eyes, which looked unusually large, were moist and filled with regret.

Hmm. What should I do?

Qing scratched the back of his neck in embarrassment, and then, "Well, now that it's come to this, I have no choice but to charge forward."

``Well, it’s true that there isn’t enough height for Ziyue to lie down, and since Iri was quite tall, and Young Lady Murong was petite, it’ll be hard for Ziyue to keep her balance.''

``There was no drop, there was a drop…….''

Murong Zhuji's expression becomes even more sad.

A puppy-like expression, as if complaining that he's hurt, um, but I like that expression. It's cute, and pitiful. Um, whatever.

``But! That was when Ciyu was sleeping.''

"yes?"

"I'm different. I really like Young Lady Murong's breasts, Miss, what's a breast? Every time I see them, my heart races and my hand wants to reach out without me knowing. Look, they're still pounding. Can you hear them?"

Now that it's come to this, let's tackle it head on.

It prickles my conscience to lie, but I can't let Young Lady Murong fall back into the personal inferiority complex she's worked so hard to overcome.

``Oh, you’re lying. You hit me last time too, and you said you were sorry while rubbing my shoulder. Before that, you patted my arm, and before that, you patted my back.''

Murong Zhuji follows closely behind Qing, and Qing's gait was very brisk for a woman, with wide strides and her arms swinging briskly.

Ximen Surin's long attempts at correction ultimately resulted in her movements becoming more graceful rather than more feminine, as this was the nature of human nature, regardless of origin.

As a result, my elbows and fists often touch Murong Zhuji-hee, but um, that was her chest. I really thought it was her arms, shoulders, etc.

"That's, uh, right, that's because I can't stroke your chest in front of other people. I mean, that's not what I'm thinking inside, right? I was like, "Oh, this was my chance to touch you naturally, but I'm scared of other people seeing, so I can't do this. My chest hurts."

It was a question of what he said without even meaning it.

It's a white lie, so it's okay, right?

``Really? Really?''

``Then. When have I ever lied to Young Lady Murong?''

``You’re doing it right now… You can’t meet my eyes when you’re talking nonsense, young lady…''

Oh, did I do that?

If he was determined to deceive, he would not change his expression and would just keep using vicious tricks, but he would just back down and act like a fool to his acquaintances.

"No, you're not? You're holding back even now, when your hand was about to go out? Oh, your hand, you have to hold it back. What were you doing, you rascal?"

Qing grabs my right wrist and makes a comical imitation of holding back my outstretched hand.

Normally, at this point, you would just laugh it off, it was the ultimate secret and ultimate skill of a skilled worldly person, a humorous joke.

But Murong Zhuji did not back down.

No, I was just waiting for this moment.

Instead, Murong Zhuji resolutely opens her front door wide.

``Okay, go to sleep.''

``Huh?''

``Don’t just talk, if you’re serious, prove it with your actions, your actions.''

He held the front of the bag with both hands and spread it out, but he turned his head away as if he didn't have the courage to look at it.

The exposed nape of the neck turned red with embarrassment.

At that moment, Qing gulped.

And then he reached out and-

Um, but something. If you touch the area under my arm, it feels like there's more flesh than this. These were bone ribs…

But if you look at it all together, well, actually, the only part that keeps me interested was that huge skyscraper in the center.

Well, that's crossing the line though.

Even when my sister-in-law was fumbling with her clothes, I didn't touch that place.

Thanks to that, Murong Zhuji-hee was anxious since morning.

It was so frustrating, like gently rubbing only the area around a scab, scratching only the itchy part and barely holding back the desperate plea that was about to burst out without me knowing it.

Meanwhile, Xue Iri was sleeping soundly. As usual, Ciyu fell asleep again when she lay down, and all that could be heard was the sound of her snoring.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

After finishing breakfast, Qing heads to the swordsmanship hall.

Young Lady Murong suddenly skipped breakfast, complaining of an upset stomach. She didn't show up at the principal's office. She seemed fine. Could she be suffering from an acute illness?

Anyway.

It's morning at the swordsmanship center. Today, too, the disciples, burning with passion for learning, send their blazing gazes.

Qing was just sorry. If I had been in good health, I could have repaid him with the same passion. Perhaps I am not worthy of holding the flute.

Qing greets him in the morning, vowing to quickly remove the fragments.

``Did you sleep well last night?''

``Yes.'' ``That’s right.'' ``I slept well.''

The Military Academy was not a military institution, so it does not require uniform military discipline in its answers.

The verbal nitpicking only happened in the first few days, and since they were more like teacher and student rather than instructor and soldier, they didn't demand any loud responses, so it was just a greeting that happened every day.

``Yes!! Did you sleep well too, Instructor!!!''

A loud voice suddenly bursts out between them.

What the heck? Who has such a cool military discipline?

Not only the Qing, but also the officials were all surprised and turned their heads to the owner of the voice.

It was none other than the nobleman of Sichuan, Gaepyeongdagu Wan Talu.

What the heck, what the hell did I eat wrong?

Since Wan Talu's dog fight was already a well-known fact not only to the swordsman but also to the entire academy, everyone was looking at Wan Talu with the same expression.

But Wan Talu, as if asking why, even his calm expression broke into a truly annoying and guilty smile, and he once again showed off his powerful voice.

``Today, the disciple I saw also wants to ask for teachings!!!''

Wan Talu's journey did not end there.

``Are you Hyung Joo? Please take good care of me, Dalian.''

He even says hello! That damn dog!

Instead of clicking your tongue and saying, "Ha, I have to hang out with such a lowly person," you should greet them politely, even using honorifics!

Of course, the name was wrong.

``Huh? I’m not Joo, I’m Yeo.''

"So you were my older sister. I didn't have time to memorize it. Now I know for sure."

And, the level of Wan Talu was not low.

By the standards of the Qing Dynasty, he was not a warrior, but a first-class warrior who was still at the level of a reserve warrior, only a mere first-class warrior, but still, at the young age of eighteen, he was a first-class warrior.

Because he was so frivolous, cheap, and untrustworthy, he was a character that was looked down upon.

No one believed in its existence, but surprisingly, it was the Wan Talu who repelled the assassin's attack.

``Hey, instead of boo-woong-boong-bang-boong-boong, how about trying boo-woong-bang-bang-boong-boong?''

``Huh? Boom bang bang boom boom?''

``Yes, since you just lost your balance in the boo-boong-boong room, how about trying to find the axis with the boong rather than the room?''

You may wonder what this means, but it was the official term for a swordsman who uses a swordsmanship that corresponds to a strong, medium, and weak swordsmanship.

In other words, it was advice to change the speed control a bit.

Why was this kid acting like this? What kind of ulterior motive was he having? Is he trying to embarrass me in some big way? The expression on Ms. Yeo's face, which had been wary, soon broke into a smile.

Well, it was a very satisfying herbivore that I swung around, so only then did I realize, oh right, this guy was also first-class.

It was a moment of rapid growth from a child to a boy, a distance of heart.

Qing, who was slowly walking around and giving a word of advice to the officials, saw the newly born Wan Talu and thought, "Huh?"

What? My child has changed?

But can it really change this much?

Well, I had a near-death experience.

The shock of hearing that the royal family was trying to kill me and that my family was throwing me away as a sacrifice to invade the martial arts world was no ordinary shock.

Thinking about it that way makes me feel sorry for him.

On the one hand, despite all that, I think it's admirable that he pulled himself together and didn't become a juvenile delinquent (though it's hard to be more twisted than that).
