\chapter{Great Instructor Ximen Qing (4)}

Qing was speechless.

\textit{No, in this situation? Release you and kill me? Giving that order to the very person you were trying to kill?}

\textit{Is that something you would say in your right mind?}

Qing finally resorted to the word "no," "no." It's a truly aggressive word, likely to provoke conflict.

"No, even if you make fun of my intelligence, you're still the dumber one. You're causing this mess by threatening to kill him, and if you tell him to let you go, he'll just say yes and obediently follow you? What on earth do you think people are?"

``You are trul a completely crazy bitch. Do you dare to refuse an order from the Emperor?''

"If the Emperor tells you to die, do you have to? What? If he tells you to just split in half and die, you can just split in half and die with your guts, right? Orders have to make sense to be obeyed."

``You, you, you dare! Who are you mocking, you, you bitch, you are truly a traitor, a high treason, a traitor! You bitch! You dare!''

It was obvious to Qing.

However, for people of that era, it was a rather radical claim.

It was a subject's duty to die when the Emperor tells him to, and the famous empty lunchbox delivery incident was proof of this.

In the past, there was a sad incident in which a scholar named Sun-wook received an empty lunchbox from his lord and, thinking, 'Ah, so he's telling me to die, a waste of food!', he committed suicide.

Wan Talu, who was about to open his mouth, stared blankly at Qing.

He was shocked by the harsh language, and even more shocked by the fact that she showed no signs of caution and showed no concern for him.

\textit{It's as if she never thought I'd harm the instructor, so much so that she took it for granted that even a slight edge wasn't necessary. That's belief. That's trust.}

\textit{Why, why? Just because I'm a trainee of the Yizheng Hall? Because I'm her trainee?}

Wan Talu had never once considered Qing his own instructor, despite the fact that he had been a hopeless trainee.

Wan Talu's expression becomes somewhat solemn.

``Did you heard that, Young Master? This bitch has gone mad. How dare she spoke such words to the Emperor! You must deal with this quickly, quickly!''

Wan Talu choose what to say to him.

"It was said that a gentleman must repay a favor he has received. Those who do not know this were like beasts. How could I harm Instructor Ximen and betray the grace of salvation?"

\textit{What the hell, you piece of shit. You're talking so clearly?}

Qing was a little surprised. Of course, he'd been writing since long ago, but he'd been unlucky.

"Are you willing to sacrifice your own selfish desires for the greater good? Grace, grace. Come to your senses, Young Master. Don't you know that every moment of your existence was a gift from the Emperor? You intend to forsake a great favor to repay a small one?"

"That."

Originally, in Zhongyuan carrying the emperor on one's back guaranteed victory, and an unconditional victory in a war of words.

"You're funny. Being born was a blessing from your parents. Why would the Emperor interfere? Did the Emperor ordered you to be born?"

"Yes, it is as you said. Young Master, hurry. This is what your father also wished. Shouldn't we repay our parents who gave us this body?"

Then there was silence for a moment.

``……Huh.'' ``……Yes?''

Tai Lingfan had a look of dismay on his face, but soon he erased that expression and became confident.

``It's exactly as I said. Didn’t Young Master, under his father’s command, enter the den of these scoundrels who dared to call themselves heroes?''

``Uh, uh uh.''

Wan Talu's eyes shook wildly.

\textit{So, Wan Talu father, you sent your son to the Royal Military Academy even though you knew that the Tongjeongsa was plotting to kill him.}

"That's impossible. If I die, the family line will be cut off—"

"Oh, you're worried about your family? Oh, I didn't know Young Master would be concerned about his family. But there was no need to worry for Young Master said, since the concubine was pregnant."

``No way.''

"Yes, isn't this a good opportunity for Young Master? In fact, if Young Master had acted properly as a son, this wouldn't have happened. But now, a woman more dangerous than Wulin has appeared. If we get rid of her, wouldn't the Emperor recognize Young Master's usefulness?"

Tai Lingfan's eyes were sharp and wide, his eyes were bulging with veins, and his mouth was still smiling. He truly has the look of a madman.

"Even if it isn't Young Master, there were countless young men who would die in your stead. The opportunity to cut off the root of future trouble lies only with Young Master. I'm sure even His Majesty the Tongjeongsa would be satisfied. Now, hurry—"

"Hey, come on, Wan Talu, you've heard everything you've heard, so I'll stop here. Talking to a crazy person will only bring harm."

Qing grabsbedWan Talu's shoulder.

"I don't care about the Wan Talu crown. How do you know what's going on with that open mouth, or what it's saying?"

"Young Master! How dare I sell the imperial prestige? Honestly, how could Young Master be a son who could be proudly shown off? Even the Great Master of Tongjeongsa, who raised him as an only child, could only sigh."

\textit{Oh, I could relate to that a bit.}

\textit{If it were my child, if Ciyu had been like this, I would have broken all his legs and taught him manners.}

\textit{However, instead of educating his son, the Tongjeongsa seemed to have decided to replace him since he was already a loser.}

\textit{He was going to throw away his son anyway, so he sent him to the Department of State Affairs to use him wisely.}

\textit{I heard that the Tongjeongsa was one of the emperor's closest associates, so he may have offered his son on his own initiative.}

"The Emperor has bestowed such grace upon such a nobleman, and it was an honorable position to be included in the Four Books as a touchstone for the conquest of Wulin! But if you refuse to die, then this is your chance. Don't you see? This is your chance to receive praise from the Emperor himself! Isn't this your chance to shed your past disgrace and become a worthy son? Kill that woman! Or kill yourself! Take your own life and prove your worth!"

Wan Talu's eyes were unfocused.

The distorted face had an expression that seemed to be one of sadness or fear.

But now, that innocent face has become like that of a young, reckless child.

Qing grabs Wan Talu's shoulders and places his chin on them.

Wan Talu, his body trembling from the frost, stares blankly up at the face of Qing who was close to him.

Her face was beautiful, and even though it was a face with clear shadows from the light of the brazier in the dark, she was simply a beautiful woman.

"Well, for now, it's best to get out of here. Don't think negative thoughts. What's an emperor or a son of a king? Countless dynasties have come and gone, and they all arose to save themselves. Don't listen to that nonsense."

"Instructor, aren't you worried? If I secretly stabbed you right now…"

``Hey. Honestly, I can’t say our Gaeppdagu is a normal guy, but he’s not that much of a bastard.''

Actually, I'm not sure if that's true.

From what I've seen so far, he's a bit of a jerk, but he's not someone who goes too far, and his evil deeds were too much.

Because I don't know if he has been piling up small evil deeds since he was very young, or if he was an extremely vicious juvenile criminal.

However, no matter how injured he is, how much of a threat can a trivial first-class brat pose?

Moreover, since Qing's senses were omnidirectional and there were no others in a narrow space, he can immediately detect any nonsense.

If I had to say, I would say it's confidence rather than trust, but that doesn't mean your skills were insignificant.

But to some, even such empty words could be a much-needed comfort.

Especially to someone who has heard that their country was trying to kill them and that their family has abandoned them.

Maybe beyond comfort-

Wan Talu's gaze regained its composure.

Not only that, but he even gave a sly, unlucky prince-like smile, but judging by his slightly trembling lips, it seemed like he couldn't shake off the shock.

"I'm fine, Instructor. I'm already a grown man, an adult, and this was it. I'm not a child, so I'm fine."

I think that even a grandfather would be shocked, let alone a child.

It seemed like the word "minor" had really stuck in his mind, as he seemed to put a lot of emphasis on the pronunciation of "not even an adult child."

Well, isn't that proof that she's a kid?

When an adult hears that they were a minor, they immediately bow down to express their gratitude, and were overcome with joy, their lips twitch, their bodies dance, and they can't help but sing along.

The only people who feel bad when they hear the word "child" were children, right?

Meanwhile, Wan Talu looks at the Great Seal with a crooked smile.

"Tai Lingfan, I'm sorry, but I'll consider your proposal unheard. They say there's no law in this world that says you have to die, so shouldn't I live? Wealth and honor are meant to be enjoyed only while living. What use iss fame after death, and what does a family that abandons its children have to do with anything?"

Wan Talu looks a bit mean.

It's Qing's personal opinion, but even if you judge it objectively, it's probably like that, because from the very first glance, he looks like a foul-tempered nobleman.

The words he spoke with that face were all about scratching at others' feelings, so this was the time for Tai Lingfan to experience the true value of Wan Talu.

"Young Master? What the-"

"If you're going to ask for a favor from someone, shouldn't you display a servile expression, hunched over with your back and shoulders, and beg like a subordinate? Tai Lingfan's attitude is so brazen, as if you're demanding me to hand over something you entrusted to me. He's such a shameless brazen man. How could I trust you and risk my life?"

``Young Master!''

"And it's truly disappointing that you so carelessly speak of other people's family affairs. In a family with a living eldest son, a concubine, that woman, Lady Yeom, was pregnant? Where in the world would a concubine's child succeed the family line? After all, after Tai Lingfan dies, who would care what I say? If I were to return to the family and succeed the lineage, who would dare oppose me?"

``Go!! You punk! Is that even a reasonable thing to say?! The great Tongjeongsa was right to lament, you truly are the greatest unfilial son in the world!''

"Well, it seems Father was displeased with my behavior, so I'll try to change things. If I become a good son, he'll change his mind and approve. It's only right for the eldest son to help with the family business. If the Emperor ever again issues such an unmanly order, I can, as a subject, do my best to prevent such a reckless plot from succeeding."

``You, you bastard, what the, what the, how.''

Tai Lingfan was unable to continue speaking.

I was so shocked that I was speechless, and I just didn't know what to do.

Isn't that a declaration that you will continue the family line and stick to the royal family, and become a spy for Wulin?

Qing looked at him and thought, "Wow, that guy knows how to scratch? This kid was a real hitter. Well, he's the kind of guy who scratches kids all the time."

"Instructor, I'll finish this one. You're not feeling well, so please get some rest."

No, this kid? Qing's eyebrows twitched.

You saved a man who was about to die, and now you dare to have my pleasure?

And you're going to eat the best part that you saved for last?

"The official said, 'I won't mess with you.' Minors were not allowed to watch, and this time, auditions were not allowed. Where?"

Even Wan Talu's eyebrows twitched.

However, he did not protest otherwise, so it was unknown what part he was upset about.

"But-"

"Enough.  This instructor have already lived and died because of that guy. This is a grudge I must settle. You're a trainee with intact limbs, so get out of here."

Qing does not prevent others from taking revenge.

Revenge was a natural right, and it was also the best medicine that allows the wronged to overcome their grievances and move forward.

However, this was not the case in all cases.

The dog's jaw was fine, and I still have countless pieces of metal stuck in it.

It's a bit strange for someone who hasn't even been hit once to claim resentment, and if he just gave me a verbal slap, then it's like the resentment has already been paid off.

"Right, right. You're going to go back. I'll close the door tightly so there's no noise. Quickly."

Wan Talu was pushed out of the underground warehouse.

Only after confirming the sound of the lower door closing and the upper door closing does Qing re-enter Tai Lingfan's room.

"Well. I'm a person who strictly keeps my word. I said you'd either speak and die in pain, or you'd say nothing and die in pain, right?"

Finally! Finally!

The corners of his lips stretch out so fiercely that it feels like they might tear apart and touch his earlobes.