\chapter{Great Instructor Ximen Qing (16)}

``Ah. The Civil Engineering Goddess. Yes, that’s right. That’s unusual, hahaha…….''

"Right? Ha, it was the same back then. You went all the way to Gwangju to find the Southern Phoenix of the Four Guardian Gods, and then you said the Jin family was in danger and you needed help. No, why would you worry about the Geodaese? You'll get back on your feet after all. Worrying about the ten generations of the Gudaese sect was the most useless thing in the world. And isn't the Jin family famous for its seaweed lilies? Why on earth do women get in trouble wherever you go? Why shouldn't you worry about yourself first…"

Well, I guess I should say this was a bust.

The Blue Dragon Dancer herself wouldn't be causing trouble, and if she was like that wherever she went, she must have a peach blossom arrow in her fortune, or perhaps a peach blossom arrow was a fortune that women receive.

"Why on earth do you volunteer to help others? Even before that, during the martial arts competition… Oh, right. You were so cool when you won, Instructor. You were really pretty. And before that, in Sichuan, some woman was flirting with you, so you were wandering around helping out at some cooking competition or something, and people mistook you for some kind of spy. And I wanted to try the ultimate mala soup…"

Hmm, Mara Ultimate Soup, that was delicious… …

But what's going on? The paths strangely overlap?

``By any chance, have you been to Xichang, Shandong, or Hangzhou yet?''

"Huh? Isn't it too far to the east? Since Master Chae So-hyeop was trying to gather all the Sasinmu, Dongcheongryong, there's no reason to look east, right? Probably."

Oh, then I guess it was just a coincidence.

anyway.

Qing organizes her thoughts.

It was originally forbidden for a counselor to give any advice to a client, but it was also a bit strange to leave it as is.

"Yeo Gwan-do, confession was not a challenge, but a process of confirmation. However, after hearing it, it seems like Chae Gwan-do has a serious problem. Instructor Lee, I think it would be better to convey your true feelings."

"But what if I get rejected? If Master Chae So-hyeop really didn't see me as a woman, or maybe he'd fallen for that girl Jeong-ga—"

"That's what I'm saying. If Chae Gwan-do was so clueless, he'd have to be told directly. And doesn't he already have a rival? How long were you going to wait anxiously for him to find out?"

``That’s… but….''

``What do you think, does it really seem like Guan Dao doesn’t have feelings for Guan Dao?''

``I don’t really know……''

"Then shouldn't we be even more certain? If someone doesn't accept your feelings, you won't just break up and go back to being a stranger. So, were you really going to wait that long, just waiting for them to understand your feelings? Your feelings, which you don't know when, where, or to whom they might be directed?"

Yeojuil lowers her head.

After a while, Yeojuil raised her head again and her expression was filled with a certain solemn determination, the fierce fighting spirit of someone facing a decisive battle.

"The instructor was right. This can't go on. We can't just keep waiting."

Hmm. That's a nice expression.

Well, no matter what, you have to live your own life.

Why waste your time chasing after someone you like while the sun was still high?

A person's heart was something that even he himself cannot control, so even if I am loved, I cannot necessarily reciprocate it.

So, we need to come to a conclusion, a decision.

I heard that you've been together since the martial arts competition, so how many years have you been together like this?

If you still have these worries, then perhaps you have become so accustomed to it that you have become insensitive to it, or perhaps you were not seeing her as a woman at all.

Qing clenches both fists and cheers.

Yeojuil nodded heavily, perhaps encouraged by that, and left the room with powerful footsteps.

And the next day.

It was Jeongsilim who had been hitting me hard throughout the training session, as if she had lost her mind and her face was covered in shadows since morning.

I asked for your understanding and called you in for special consultation because your condition looked really bad.

"Jeong Gwan-do. Is something wrong? I can't seem to concentrate today."

Then, as if it had been waiting, a stream of tears fell down again.

Qing was surprised.

``Jeong Gwan-do?''

``How, how could you do this, ugh, leaving me behind, right here with me, that bad girl Yeoju, it’s too much…….''

It was the official who burst into tears no matter what.

Qing became a little, no, a lot more embarrassed.

Ah. Yeojuil Trainee, the confession attack was successful.

But where there was a winner, there was a loser.

The two followers of the Blue Dragon Dancer Chae Seong-ha were Yeoju Il-guan and Jeongsil-im, so if one of them succeeded in confessing, wouldn't one of them inevitably fall out?

As the person who provided the main cause, well, I guess I couldn't help it, but if I went back to yesterday, I would give the same advice.

But because she was crying so sadly, Qing spread her arms wide. He couldn't just sit by and watch a woman weep, could he?

Then, Jeongsilim Trainee suddenly hugs him.

It's a bold move to dare to dig into the arms of an instructor, who was not a teacher as high as heaven, but was roughly equivalent to an instructor.

Sob, sob, sob, then… … .

And pat his head to calm him down.

So, I hugged her tightly and said, "Ugh, this bitch was trying to catch a person." But since I had the shrapnel removed from her body every day, I guess I can say that she's finally able to bear it without having to pretend to be in pain.

First of all, I guess it's my karma.

How much time has passed like that?

``I’m sorry, I’m sorry. I’m so embarrassed…''

"It's okay. People were naturally designed to cry when they're sad, and that's how they can find relief. So, being able to cry when you need to cry was also a skill, right?"

Jeongsilim responds with an embarrassed smile.

Of course, it would be embarrassing for a grown woman to cry like a child.

"Yeojuil, that's it. This shouldn't be happening. It's so fatal, isn't it? We didn't say anything, but we left it up to Prince Chae's choice. A promise, a promise without a promise? How should I put it? Something like that—"

``Couldn’t it be an implicit agreement?''

"Yes! That's right! That! A tacit agreement! But how could it be, how could it be so vile, how could it be so damned, ugh, unforgivable."

This was the real truth that goes on and on.

You were crying earlier, but now you're really angry.

I was wondering what Qing would do about it.

Era, I don't know. This was the Zhongyuan.

"So, Jeong Gwan-do was just going to give up? Without even trying to convey his feelings to Chae Gwan-do? Was that all Jeong Gwan-do's affection was?"

He had a fantasy of an exclamation mark, a symbol that did not yet exist in the Zhongyuan, appearing above Jeongsilim's head.

If it were my hometown, it would be a huge problem, but isn't this the land of the Zhongyuan, a world where one man has multiple women?

"That's right. This isn't the time for this. I may be a step late, but the wedding hasn't even taken place yet. It hasn't even been decided who's the rightful wife yet, right?"

As she speaks, a cold and dreary look of war lingers in Jeongsilim's eyes.

Qing, um, how should I put it, it's a bit sad.

Someone tried to enjoy some behind-the-scenes sex on an electronic game and ended up with a woman without a penis. What's so bad about choosing a woman on a game, you bastards, you fucking world.

And this bastard Chae Seong-ha, he already has two women, he's such a lucky bastard, just get the hell out of here.

It was when Qing was spewing out such evil words to Chae Seong-ha, who had done nothing wrong.

"Uh, instructor? By any chance, can I call you 'sister' in private?"

"yes?"

Qing asked back.

``No, please excuse me, I didn’t hear that. I was wondering if this would happen if my sister was around…''

Isn't that the problem?

Jeongsilim Trainee, twenty-six years old this year.

Of course, that didn't mean that Qing felt burdened or embarrassed, since she had to do some calculations to reveal her age anyway.

So, since the martial arts competition officially started, I'm considered to be twenty years old, and how many years have passed since then?

I think my real age was much older, but why was everyone like this? Is it because I can't help but act old?

Even Zhuge-i and Lady Murong tried to call her "sister" but then changed their minds to "young lady." Oh, I wonder if Lady Unaram and Lady Unaram in Guangxi were doing well. I wonder if they're still noisy.

``If it’s private, then yes. I’ll allow it.''

Although Qing didn't realize it herself, she used to jump up and down and rub her arms to calm her goosebumps whenever she heard her older sister's voice.

Well, humans were creatures of adaptation, and being treated as a woman has become as natural as breathing, so it feels new to me now.

"Yes, Unnie. Actually, you've been so amazing since the finals of the Jamryongbimuhoe, I've always wanted to become a female martial artist like you. You're my idol. And you're so pretty, too. Wow, how can your skin be like marble?"

For reference, marble refers to the best of the white jade, and only the white jade mined in Dali County, Yunnan Province, was called marble.

This was also the origin of the term marble being called marble in the homeland of the Qing Dynasty.

``Ahaha, Jeong Gwan-do was also pretty.''

Although he was used to being treated like a woman, Qing was still not used to the way women talk and the endless compliments they showered him with.

Well, to be honest, it's difficult.

Originally, I should have gone into detail about what was pretty after this, but I tried to praise it by pinpointing what was pretty, because Qing was much more beautiful herself. The picture ended up looking a bit strange.

"Jeong Gwan-do, I have another appointment scheduled, so unfortunately, we'll talk about it later. And since it's only in private, I understand what you mean, Jeong Gwan-do."

In that way, Jeongsil-im also walked out confidently with powerful steps.

And the next day, morning.

In the guardhouse annex of the State Council, Chae Seong-ha and two women knelt side by side.

Qing, who came running after receiving a call from the security guard in the morning, was absolutely shocked.

``Trainees. Please.''

The three officials bow their heads deeply to him.

All three of them had turned a deep red, and even the ears sticking out from their drooping heads had turned bright red.

``No, no. I don’t mean to meddle in the affairs of a man and a woman, but if sparks fly between a man and a woman, that could happen, but still, sneaking out in the middle of the night is a bit much.''

The State Affairs Academy was an educational institution, and even though its location was in the center of political sphere, its security was not lax.

It was only during the three idiots' time that they requested in advance that they be removed from patrol towards the swordsmanship hall due to special activities at night, so even though those idiots of the blood sect shouted loudly for Mahou-sama, they could impersonate him without worry.

Otherwise, the swordsmanship hall would be visited by the patrols of the Wulin Alliance warriors.

And there was a truly embarrassing secret meeting between officials who had sneaked into the warehouse last night, so the men and women arrested at the scene were locked in a separate room for the time being.

It was a bit of an ambiguous situation.

It was a clear violation of the rules to come out at night and hide in the warehouse, but that doesn't mean there were any rules prohibiting dating or contact between men and women in Yizheng Martial Study Hall.

They were all adults, and it was not the place for the Department of State Affairs to interfere in matters between adults.

So, I sent a message to take him to the instructor in charge.

Well, yeah. It's a fiery affair over the rightful wife, well, that could be it.

Chae Seong-ha, you envious kid… … .

Qing sighed deeply.

"Well, um. There's nothing wrong with couples having fun together, but then again, we don't have separate rooms. There should be a vacant room in the north wing, so I'll make arrangements for you to take care of that after work."

``……Yes.'' ``……Yes.'' ``……Yes.''

It's an answer that crawls in because it's embarrassing.

Qing sighed again.

``Also, enjoy your practice without disturbing others, and pay special attention to contraception. If you have a child, won’t it greatly interfere with your practice?''

``……Yes.'' ``……Hehe.'' ``……Irony.''

It's a very unattractive reaction, though.

Well, since it's come to this, it's something they should take care of themselves.

But last night. How did I end up sleeping so soundly? I couldn't sleep, so I wish I had taken a walk around the swordsmanship hall.

There was a little commotion that morning though.

Today was the day that Sojeo Geomok-gun joined as an official assistant and carried out the instructor group's schedule.

In fact, I was secretly on the instructors' side as an unofficial assistant before, so there was no difference.

And in the evening, there was the return of Sima Chunfeng, who had gone to deliver news to the Wulin Alliance.
