\chapter{Great Instructor Ximen Qing (5)}

In any activity done together, it was only fun if the other person matches well with you.

The same goes for the Qing massacre.

There was nothing more frustrating than when the other person was so stubborn that you just pulled out a fingernail and they start crying and blaming themselves for their mistake and begging for forgiveness.

I should at least pretend to hold on a little.

How disappointing it would be if someone could commit evil deeds until they were so full of evil karma that they could barely bear the slightest pain.

The opposite was also true.

If the other person was so stubborn that he or she doesn't give in even though he or she feels like he or she will die if he or she continues, he or she will become very gloomy.

Since ancient times, this ending has been a place where the wicked were rewarded for their past actions.

It's not a feat to die painfully, but only when the mind and soul were completely destroyed can one say that one has met a proper end.

And what if you don't even have enough time to deal with someone who doesn't even regret his actions?

"Kuuu, you bitch, I can't wait for your end. I know people like you. You'll be begging for your life, shitting and peeing, and spreading your legs wide."

``Oh my, it’s so poisonous.''

Qing sticks out her tongue.

Despite giving it his all, Daeyoungban was still alive and kicking.

Even if you peel the skin, slowly break the bones, grind the body's extremities on a stone floor, and tie up the limbs nicely, it's still not very swollen.

Either the pain threshold was too high or something.

Or maybe we're just turning our pain into anger, and we have more narcotic neurotransmitters in our heads than others.

Or maybe he was truly innocent, and despite the pain of his body, he was not afraid of death, of his own afterlife.

``Keu-khu, ugh! Gulp! Kkuu-khuu……. Is that all?''

Hmm. He's a strong opponent, he's a strong opponent.

Qing unconsciously crossed her arms, then frowned in pain from the unhealthy posture, then let her arms hang down awkwardly and looked around for a moment.

This, that's it. Um, well, that. I don't remember the term at all, but it's from liberal arts psychology.

People were basically reluctant to admit their mistakes, right?

So I try to avoid my mistakes in many ways.

Among them, there were those who had this religious blind faith, who firmly believed that their actions were necessary, noble, and righteous.

For example, the world can become a better place if the wicked suffer a miserable end with immense pain, so why would someone endure such terrible torture with such a heavy responsibility? Well, it hurts a little. Why am I attacking myself? Anyway, well, yeah.

I didn't mean to go this far.

Qing wiped her hands clean and took out a jade tablet the size of a palm from her bag.

Then, she slowly lowered it to Tai Lingfan's eye level, who was stuck to the floor with his limbs tied in knots.

``Kuuu, what else……''

Daeyoungban's voice, which had been laughing and saying, "What kind of nonsense were you talking about again?" suddenly stopped.

The Empress's identity badge. Genuine.

The Emperor's companions were permitted to have one Marquis, three wives, nine concubines, twenty-seven concubines, and ninety-one concubines.

So, just as there was only one emperor under heaven, there was also only one empress in the world, and she was truly the mother of all people.

``What, what is this, why……''

The Emperor's companions wore phoenix-engraved badges, but each had different numbers and lengths of feathers, different numbers of extended claws, and different postures. This was the strict law of the imperial palace, and the strict distinction of status ordained by Heaven.

Daeyoungban desperately examines the pattern.

It can't be, it can't be, even if you desperately repeat it and examine it, isn't even the act of daring to doubt its authenticity an act of blasphemy?

In fact, it was something that Qing didn't want to use unless absolutely necessary.

\textit{Empress Mama, um, that's right. I can't do anything recklessly. But, after all, it was given to me by Her Majesty to use, and since he's going to die anyway, there's no worry he'll go around talking about it, right? This is justified in the end. Hmm, did I bring it up for nothing…}

It was a moment when Qing became a little uncomfortable.

The sound of Daeyoungban shouting as if he was trying to change that feeling.

``You, Seochang’s, Seochang’s woman! But why, how could Seochang interfere with the Emperor’s event?''

What about Seochang? Since Dongchang was Dongdong, does that mean there's one Dongchang, Seocheong, Namchang, and Bukchang in each of the four directions? Hmm, then it seems a bit pitiful for Namchang to belong to that direction.

Well, given the circumstances, I think it might be a group that has connections with the Empress Mama.

"You bastard! You have revealed your crimes. It is traitors like you who are eroding the nation and leading it to ruin. Isn't this a crime that deserves death?"

Qing shouts in a stern voice.

``What, why should I-''

"Punishing Wulin? There are already tens of thousands of martial artists in this country. If you are to punish them, would they simply sit idly by and die? If they were to rise up with a sword to survive, what would the state of the country be like? What chaos would there be? Do you think the foreign enemies along the border would just watch? You're a delusional bastard intent on leading this country to ruin!"

"That-"

Daeyoungban opened his mouth wide.

Because it's not wrong.

It was also the reason for the plot in the imperial family.

A trick to gradually weaken the power of the martial arts world under the pretext of a legitimate cause.

In the past, in Sichuan, they tried to erase the Sichuan Dangga by accusing them of treason, and this time, they wanted to block the Uijeongmuhakwan, punish those involved, and put pressure on the Wulin Alliance to weaken its power.

This was precisely the reason why we cannot suppress them by mobilizing the military or using trickery.

"So, does that mean His Majesty should ignore those human bandits and thieves? Should we fear them, who dare to defy the will of Heaven?"

"You fool! Officials who depend on the Emperor's allowance exploit the common people to fill their own stomachs, yet these pitiful commoners instead praise and exalt Wulin as chivalrous warriors. If the Emperor were to purge these officials who were eroding the nation and, with fairness and mercy, bestow virtue through policies, the common people would naturally turn their backs on Wulin and praise the virtues of the Imperial Family. Then, wouldn't even these Wulin people be able to embrace the Emperor as loyal subjects?"

Daeyoungban opened his mouth again.

Well, it was a moral delusion that if you just do well and everyone will be happy, there was no alternative because it was a good thing that anyone can say and cannot be refuted.

But if you refute this, then you become an immoral person.

"In the past, Emperor Yang of the Sui Dynasty invaded Liaodong out of personal grudge, only to be defeated three times, resulting in the downfall of his nation. In the past, Hailing of the Jin Dynasty invaded Song out of personal greed, causing the nation to be shaken to the brink of ruin. You, a self-proclaimed loyalist, wish to lead the way on this path to national ruin. Are you not a group of treacherous traitors, the likes of which were unparalleled in the world?"

``I just, given orders-''

"Shut up! The Qi Dynasty's Yu Ji risked his life to offer advice to the King of Wei, who, recognizing this, revived the Qi Dynasty. The Tang Dynasty's Wei Zheng opposed Emperor Taizong's edicts hundreds of times. During his lifetime, he laid the foundation for the nation. After his death, the nation was in peril, and Emperor Taizong longed for him. Isn't this what true loyalty means when it risks its life to offer advice?"

If Ximen Surin had heard it, it would have been a very satisfying speech. 'That thief taught very well,' she would have thought.

Even if you study abroad, you can say that you learned something from me. That's a satisfactory thing.

Qing was a woman who graduated from Hanlim Academy.

"You dared to use the Emperor's name to slaughter innocent people. This is a scheme to dishonor the Emperor's name. I will kill you, exterminate your entire family, and report you to the Four Books of Death, leaving you a criminal forever. Your name will be remembered as a subject who dishonored his lord."

``Wait, I, I just sincerely-''

``Shut up. What does your loyalty have to do with it?''

Qing gives an evil smile.

"Fabricating detailed evidence is all I need. You will be labeled a murderer who exploited the people for personal gain, raped and murdered countless women, and a treacherous official who dared to use the Emperor's name for personal gain. I will make it so. The world will call out your name and spit on it. Congratulations! You will succeed in etching your name into history."

I will make it like that, I will make sins that were not there and turn them into the world's bastards.

If he was someone who endures the pain of his own body and his own death, he was probably someone who pursues values other than life itself.

Well then, just trample on that value.

Only then does fear begin to appear on Daeyoungban's face.

This was outrageous, there was no outrage like this in the world.

What have I done wrong? I just want to do my best, for the Emperor, to repay the favors I have received from him.

``Ahhh!!''

Qing suddenly stomps on Daeyoungban's sprawling arm and the blunt back of his hand with his fingers torn off.

Look at this, the volume of the scream was different.

She picked up the jade tablet in the same state that Qing had trampled on, cleans it well, and puts it away.

Well, I don't think she gave me the jade tablet for this purpose, but I'm sure Your Majesty the Empress would understand, right?

Qing-i was humming, her voice buried in the muffled screams, but no one but herself could hear it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing's face was very clear and refreshing as he opened the iron door of the underground warehouse and came out.

Just looking at his expression, you can't imagine that he's the one who swelled up with revenge and had a thousand pieces of metal embedded in his torso.

``Tsk. Don’t go around laughing like that.''

``Huh.''

What was happening underground was nothing short of torture and murder, nor was it a justifiable act. Furthermore, the perpetrator was the divine dragon of the Orthodox Wulin, the Heavenly Blossom Sword, so it was only natural that the Qing's acquaintances were guarding it.

Pang Dae-san took out a handkerchief and wiped Qing's face, then dabbed it. The blood wasn't just blood, but a clump of human fat, making it difficult to remove.

``Ah. I guess it got on me face.''

In the past, she enjoyed the burning sensation that made her face feel hot, but after training in the Ximen Surinryu Beauty Walk, she instinctively avoided it.

Because the moment she walked around with something on her face, she could get hit by a sudden, sudden drop of nuclear noogie.

Still, the blood splattered on her face, which was why she was so excited and enthusiastic.

Well, the last one was especially fun.

He said it was a misunderstanding and that he had never thought of it that way, and that he couldn't actually pray because his arm was crushed, but he was going to do something about it anyway.

He stretched out like that, but it was funny anyway.

``…Don’t do that again.''

``Huh? What?''

"There was no need for you to stop Heaven-shaking Thunder Bomb. Besides, that was the misdeeds of White Hand Witch, not your own."

That's right.

The one who blocked Heaven-shaking Thunder Bomb with her body was a witch who suddenly appeared, not Heavenly Blossom Sword.

Well, that's true, though.

"Hey, if I can, I should. And what, would I feel better if I avoided it? Even if I have to suffer for a while, I feel better if I can handle it. Besides, if it didn't work out, I wouldn't have even tried. After all, my life is the most precious thing to me, you know."

At that, Paengdaesan's expression suddenly turned sour.

Qing nudged him with her elbow.

``Oh, that’s wonderful. You even worry about me.''

``That bitch who knows-''

"What? San! Did you just call me a bitch? No matter how close we are, now it's getting to the point where we're swearing at each other, right? Even though we're close friends, we haven't swearing at each other yet."

A vein bulged on Paengdaesan's forehead.

Qing was giggling and making a fuss.

Well, what's the point of talking about it seriously?

Don't do that in the future, because then I'll have no other answer than "I'll try my best."

Good things were good, and there's no reason to bicker and get upset over something that's already been resolved.

Even though it's a long summer, it's already getting dark.

I had an early lunch and went downstairs, so I was so absorbed that it was almost 4:30, and I didn't even realize how much time had passed. That thought suddenly occurred to me.

Hmm. I'm hungry.

Even though my insides were swollen, I was still hungry, ah, I was going to have to eat some water anyway… … .

Qing's shoulders slumped.