\chapter{Great Instructor Ximen Qing (12)}

The three members of the Blood Cult Infiltration Team have clearly reached second-rate status since their departure.

Because he swallowed that huge elixir and used the master's true technique to open up the blood vessels throughout his body, his circulation was smooth.

Whether it was due to the nature of the main ingredient, the secret recipe of the manufacturer, or the fact that the elixir itself was so large that it was difficult to swallow in one bite, the quantity of the elixir itself was already above first-class.

However, martial arts were a purely personal achievement, so if you can't unleash your sword spirit, you'll remain second-rate forever.

But the difference between a third-rate drone and a second-rate drone was huge.

Third-rate warriors have their bodies filled with energy through tonap and chukgi, so they become very healthy and strong commoners.

Of course, that doesn't mean they can be compared to commoners, since they know how to handle weapons and don't hesitate to hurt people.

However, from the second level, where the dantian was completely established and the energy pulses extend, the strength, endurance, reaction speed, hearing, sight, touch, etc., all grow significantly due to the betting, and from here on, a complete difference was shown between them and the common people.

So it's only natural that the trio's achievements were clearly rising.

But? The achievements went up?

"Brother Joe, congratulations on your accomplishment. It's embarrassing to call you brother now, since you're still struggling. By any chance, do you have any secrets?"

``Well, it’s talent. Do I really need to ask?''

``……?''

"In the end, it all comes down to talent. Those who were meant to be experts will eventually become experts. What's the secret? If you have talent, you'll get there in no time."

The rest of the story was omitted, but even if you don't listen, isn't it saying that someone without talent, someone like you, was no good?

``……''

``Why, do you have something to say? Well, I guess I have something to say.''

``Where were you going?''

"I need to swing my sword one more time. If I just sit around after work, I'll just stay in the same place."

Jo Hyun-il then heads outside.

The remaining pipes were so absurd and unpleasant that I clicked my tongue.

``Huh, I’ve never seen people like that before.''

Although Jo Hyeon-il was usually quiet, he was gentle and docile, so the shock to the officials was great.

It's true, but it's strange that people change their expressions and attitudes immediately after achieving something.

It was an attitude that would make Qing click his tongue if he saw it.

How can anyone know what tomorrow will bring? And since everyone's martial arts achievements were different, isn't it a realm of unpredictable enlightenment where even someone who was inferior to me today can become a master tomorrow?

Even if that's not the case, you can enjoy a brief, low-level sense of superiority by ignoring and insulting them, but what good was there in making enemies?

However, the officials were not greatly disappointed or shocked, so there must be more than one or two such people in the Zhongyuan.

That's the kind of guy he was originally.

The official shook his head, lay down on the bed for a moment, then sighed deeply, picked up his wooden sword, and went outside.

I feel dirty so I need to practice.

In the end, I would say it was a positive result.

Anyway, I just misjudged the person, and I had seen countless people who would act badly and make a fuss just because their martial arts skills were a little higher.

This was especially true for the second- and first-class martial artists, but truly renowned masters display their dignity through a polite and generous attitude.

It's the same in Qing's hometown, wouldn't it be perfect if you turned martial arts into wealth?

There were many who believe that having more wealth means they have the right to ignore and insult those who were poorer, especially those with ambiguous wealth.

And the characteristics of these guys.

To those who were superior to me (whatever my true feelings may be), I become cowardly, bend my back, and speak with a hushed voice.

So, it would be natural to be respectful in front of the Heavenly Blossom Sword (known as the ultimate master).

``Instructor, I heard you were seriously injured in the final battle with Sosumahu.''

Look at this? Qing smiled elegantly.

By the way, Qing's smile was not elegant.

Just as her brisk gait is, her smile was also brisk, and when it comes from the heart, it becomes a field of flowers in full bloom, dazzling and splendid, stealing people's souls away.

However, I have learned and mastered the elegant smile of the Ximen Surinryu beauty, the slightly frowning, shadowy smile that has been the eternal ideal of the people of the Zhongyuan since the appearance of the West Poetry, so I know how to fake it.

So, the more elegant the smile becomes, the more it becomes a smile that was created with a sharp edge.

Hey kid, what's with the small intestine?

What kind of bastard would dare to exalt Sosu Witch, who was a terrible human butcher, the greatest of all demons, and the representative of the most demon-like demons?

Normally, I would have just thought he picked it up somewhere, but now that the guy I was watching suspiciously said it, it sounded more meaningful.

Didn't the White Hand Witches do it because they were members of the Blood Cult?

The Blood Cult guys call the Subsimmain the Demon King or something, so wouldn't they be calling the Minor Witch the Minor Demon King?

``I heard that the pro-Kim was quite powerful. Are you feeling alright?''

It's not a pro-invasion mirror, but rather an infiltration mirror.

"This instructor was still recovering. However, since he was doing his best to resolve the situation, the authorities can rest assured."

"How could I not worry? My most respected instructor, Professor Ximen, was in danger from that terrible poisoning. My anxiety was so overwhelming that I can't even sleep. Just thinking about it brings tears to my eyes, blinding me…"

It's a bit of a rant, but it's a concern of mine. And there should be only one or two people around Qing who were raring to go, so this was pretty good.

So, Qing's head tilted slightly.

Isn't that right? Is it just a misunderstanding? I've heard that counseling these days has become less and less sleazy. Could it be that it's just a government that's been exploring the weak and weak, and the weak and …

``So, I, this…….''

``Hmm? Joe Kwan-do? What was this?''

"This was a family elixir. It's the Life and Death God's Life and Death Yosangdan, said to cure any internal injury. I hope Instructor Ximen will accept it…"

Saengsa Shinui was a person from about 500 years ago, and as you can tell from his grand nickname, he was considered one of the best doctors in the medical community.

As a female doctor herself, she had Langzhongdaein read the medical book of the God of Life and Death, so she knew well the status of her senior.

It was also used as an expression similar to Hwa-ta.

Even Hwa-ta can't save this.

Even the god of life and death cannot save this person.

``No, what was this all about…….''

He made an appointment for a consultation because he said he had something urgent to tell me.

Since countless requests for consultation have been pouring in lately, I assumed that 'I have something to tell you' was also a request for consultation.

I didn't know it was a tribute.

but.

"I understand your feelings, Instructor Cho. However, I cannot accept such a valuable item, so I will simply accept your sentiment."

Qing expressed his intention to refuse.

One, Qing was not shameless enough to take the heirloom of a ronin with no background or proper teacher and eat it, let alone the liver of a flea.

Second, it was against professional ethics for an instructor to receive such a valuable item from a trainee.

And above all, because it's suspicious.

Yosangdan was a general term for herbal medicines that treat internal injuries. Internal injuries were a realm of internal medicine, so they were not made with general herbal medicines.

That is, it basically belonged to the elixir.

No matter how much I tried to tell them to go, was there any reason to keep the elixir and remain third-rate?

Besides, if it's an elixir given by someone who took strange medicine and simultaneously achieved both enlightenment and evil deeds, it's suspicious no matter how kindly you try to look at it.

``No. Please don’t refuse. I’m just so heartbroken, I can’t seem to continue practicing.''

"If it's the upper level of the God of Life and Death, it's like a spare life. The government doesn't hand out such a precious item so carelessly. It could be dangerous. But I'm truly grateful for your kind heart."

``Well, I mean, you don’t seem to know, but this was a great elixir in itself. Not only does it heal internal injuries, but it also allows you to glimpse the next level, Instructor.''

``I know this, too. It’s a precious item, so I can’t accept any more.''

At Qing's refusal, Jo Hyeon-il looked clearly embarrassed.

Well, I never even imagined that I would be rejected, wasn't that what Team Leader Dan did in the first place?

There was no one in the world who would refuse an elixir, and if you don't give it to them, they will try to take it by force, so they will go crazy and swallow it whole.

``Please, if you accept it, my heart, my heart was not at ease!''

"Even if it makes me feel a little uneasy, I keep it. It's a treasure I must keep."

``It’s so uncomfortable! Please!''

``No, I said it’s okay-''

``No! You have to take it!''

It's like giving and receiving.

It was a tense push and pull between those who desperately wanted to put it in their sleeves and those who didn't.

And then finally.

``Eight, I’ll leave it here!''

``The official? The official Jo! The official Jo Hyun-il!''

It was Jo Hyeon-il who ran out without hesitation, leaving behind his wooden box.

Qing, take care of the wooden box first, because it's getting more and more suspicious.

Are you forcing me to give you such a precious item?

Besides, I don't mean to ignore you.

What if someone who lives day to day on a short-term contract has a golden calf that has been passed down as a family heirloom?

And you give it to someone else?

No matter what, it's still weird.

But if it's the work of the Blood Cult, it makes sense. Like before, it's something like a parasitic salamander or something poisonous.

Qing opens the wooden box.

It wasn't as red as the Jamramdan I saw back then, but rather, an unusual medicinal scent seeped into my lungs, refreshingly. Hmm, it didn't smell like blood or meat, but I don't know…

Qing stares blankly down at the pills for a while, then picks up a hand mirror.

I don't know. You'll know once you try it.

If it's poison, it'll spread a wonderful, refreshing flavor, and if you've heard of a parasitic salamander, the bottle will make a friend.

The reason bad karma increases was because good karma was a little bit more than bad karma.

And if it was all my misunderstanding, and if it was truly given with good intentions, wouldn't it be enough to pass on at least one of the ownerless divine skills?

And then, Qing took the medicine in one gulp.

The moment it enters your mouth, the fragrance explodes.

As was often the case with elixirs, it melts away, going down your throat naturally as if you were inhaling its fragrance, and a refreshing feeling spreads afterward.

Check the mirror. No abnormalities.

Then I didn't hear anything strange… … .

Qing sits cross-legged and leads the energy.

The true energy, which was filled with medicinal properties, started from the dantian and spread throughout the entire body, as if gently caressing the eight meridians that had been disrupted by the rampage of the Heavenly Demon Energy.

What was this? It's really good medicine.

Oh, I ate it for nothing. I should've kept it and fed it to my kids when they got hurt. I'm the type of person who just soaks it in water and leaves it alone anyway.

But I already ate it.

So, why don't you take care of it properly and celebrate it properly?

It was during this time that Qing was concentrating on absorbing the upper class.

Suddenly, a strange sensation was felt in my stomach.

A small, slender creature stretches its legs, and Qing carefully examines its shape with his senses.

A round but broad head, a pointed, hooked tail, and four small, blunt, and somewhat crudely shaped feet.

This bottle, um, yeah, I think the name would be a wine glass. It can double the strength of alcohol.

Well, I guess you could call it a huge gain.

But profit was profit, and Qing's eyebrows twitch as he closes his eyes.

You little shit, you're feeding me parasitic salamanders?

Well, there was a time when I lived on bugs worse than that, but, well, thinking about that time makes me feel a little hungry.

That was the moment.

Two parasitic salamanders meet in Qing's stomach.

I guess there's a bit of a weight difference between the two.

Well, being a drunkard was no longer an ordinary person.

It was a bottle of alcohol that had been filled with all kinds of poisons that the blood poisoner had accumulated, including plant and animal poisons, paralysis and acid reflux, the poison he once enjoyed, and even the poison accumulated from eating rotten meat.

Seeing a much younger fellow suddenly appear, he approached him with a happy expression-

Oh, what, you two were trying to be friends?

-The bottle opened its mouth wide and hit the glass on the head.

``Huh.''

Qing lets out her characteristically stupid exclamation.
