\chapter{Great Instructor Ximen Qing (8)}

Is fifty points for bad karma a low score?

Oh my, if I get fifty points for going out once, I'll get one hundred points for bad karma if I go out twice.

Then the bad karma becomes more than 100 points?

From then on, it was a realm of divine punishment, and those who lived in sin could not be wronged no matter what happened to them.

The potential enemy molecules that the Qing can enjoy by tearing, tearing, chopping, boiling, and blanching to their heart's content were treated as useless parasites in the world.

But, how did this evil karma come about?

Did you take advantage of the commotion caused by the assassins to commit some bad deeds?

But what makes no sense was that if three people have a combined score of 150, it means they committed a complete massacre.

No matter how chaotic the situation was, there was no way something like that could have happened secretly.

Or did you harm a virtuous person?

Qing looks back and forth between the three people who have suddenly reached a dangerous level.

It was a betrayal by those who had been quiet and had nothing particularly noteworthy to say.

Why, wasn't there a type of person at school who just quietly drifted away, like water mixed with water or alcohol mixed with alcohol? That doesn't mean their grades were good or bad, but rather,

Hmm. Grades.

Qing's eyes narrow even more.

The sound of the swinging wave, boom boom boom, was quite heavy and solid. Wasn't it because the swordsman was not this skilled?

Of course, you may have gained some insight through the leisure time you had while out.

In Buddhism, it was called emptiness, and in Taoism, it was called nature. In order to fill, you must empty yourself, or do it naturally without rushing or rushing your mind.

But once doubts arise, the suddenly grown sword power also becomes extremely suspicious.

But what if they were originally second-rate guys, but they evolved into first-rate?

The swordsman's classes were non-internal arts classes, and the use of internal energy was prohibited in order to train pure swordsmanship skills.

First-class was the realm of the sword spirit merchant who can externally display the sword spirit, but since the use of internal energy was prohibited, it was unknown whether it was actually achieved or not.

Unlike second-rate martial artists who have to concentrate and exert themselves to barely calm their internal energy, when you become a first-rate martial artist, your internal energy will flow naturally.

As your internal energy flows, it naturally adds strength to your muscles and bones, so when you reach a first-class level, you will experience great development in your physical strength and muscle power.

And, Qing had been through something similar before.

Qing's gaze turned elsewhere.

Wang No-pil, a muscular giant who swung his sword while sweating profusely, was a master of the stone fighting technique (chair fighting) who had entered the Uijeongmuhakkan after being injured in the finals of the Jamryongbimuhoe.

He was also a person who had fallen for the previous blood cult's trick and swallowed a pill of loneliness.

Was that the Jamramdan? A terrible potion made from grinding people. And parasites were added to it.

Then suddenly a thought occurs to me.

Didn't they say that loneliness was like a suicide order, spewing poison and causing terrifying pain?

I don't know because I haven't been sick, but even Miss Mo-yong rolled her eyes, arched her back like a bow, and trembled all over her body, as if she were going to die.

Can't a drunkard do that?

Since it's been eating so much poison, it must have evolved or something. It's said that spirits grow by eating poison.

Hey, bottle, try that. That.

Of course, something like a dramatic exchange between humans and loneliness did not happen.

If I could understand what people were saying, how could that be loneliness? Even if it wasn't spoken, I was just thinking it over in my head.

As expected, it's a small thing, so words can't describe it.

Qingi's inner strength was driven by a stab in the side of solitude.

The parasitic salamander spews out all its stored venom, saying, "Oh my, here we go again," and a chilling, hot, and spicy venom spreads out.

Are you sick of poison? To me, it's just like sweet alcohol. If you eat everything without discrimination, this was what happens.

Hmm, the liquor bottle, it's growing for this taste.

However, this was not the reaction that Qing had intended.

This time, Qing raised the stakes and tried to press down on it.

The parasitic salamander let out a sad, dying scream, and I felt a little sorry for it.

I don't hear it at all.

If we feel sorry for parasites, should we also feel sorry for blood-sucking mosquitoes and fleas?

I should be grateful that they're raising me well, feeding me good food, so why can't my solitude do the same? I heard that the solitude of the person next door was very devoted to serving its owner, and that it's rumored to be the world's most filial son, no, a filial sage.

That was the moment.

As the drunkard gapes open his mouth in fear of death, a sound from a realm that humans cannot hear spreads out.

``Ah.'' ``Ugh.'' ``Ugh.''

Three bodies fell at the same time as if they had been put together.

Oh, the bottle! You were a kid who did it when you had to!

The pain was only momentary, however, as Qing immediately withdrew his bet and the bottle stopped bothering him.

Ta-da! It just so happened that class was in the middle of it, and the afternoon class was sparring, so one of them, Officer Jo Hyeon-il, got hit hard in the thigh and rolled around, clutching his leg.

Hmm. Did I do something a little embarrassing… … .

Qing's eyebrows curved in the opposite direction.

In my hometown, there was a law called the presumption of innocence, which meant that someone could not be arbitrarily identified as a criminal until conclusive evidence was available.

It was still unclear whether he swallowed the nasty drug that was injected into his body knowingly or whether he swallowed it unawares like our gang of ronin.

``Hey, were you okay?''

``Huh? Hmm?''

The other two, let's see where they were, Jang Seol-kwon and Chu Jo-hun, the two of them just stood up with a puzzled look on their faces and dusted themselves off.

It was strange. It felt like I'd just suffered some terrible pain, the kind that left me paralyzed and nearly collapsed. But now I'm fine. Was it an illusion? No, it felt like I'd truly experienced hell. With that expression, he just blinked, blinking.

Well, what should I do with this?

I think we can only make a judgment after we find out whether these guys knew about it and ate it or not.

If you ate it without knowing, you could just beat them up like last time and think, "Those blood cult kids were up to something again."

If you knew and ate it, things would get complicated.

If I were to ask them what they ate, and whether they knew it was a human-made elixir, they'd only respond with, "Of course I don't know. Huh? Blood Cult? I'm an individual."

While I was in the school, I was already familiar with the tricks of handling a rat in a bottle of alcohol, so I could subdue it right away if necessary.

If you suddenly collapse and tremble in pain, it means there was a mole in the blood sect somewhere in the school, so you can turn it upside down.

If the Blood Cult bastards want to reveal their true colors, they'll have to make contact with the authorities, so you can tail them on their next outing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The so-called Laosan Assassin and White Hand Witch Riot Incident left countless victims.

First of all, there were residents of Laosan County who suffered property and health damage, but the Wulin Alliance has already begun damage assessment and recovery efforts.

And there was a wounded Qing.

What about the damage to the swordsmen and officials that resulted from it?

Since it also interferes with the personalized posture correction provided by the Heavenly Blossom Sword instructor, the quality of the education that should have been received was bound to decline somewhat.

However, this damage was minor.

There was a truly great loss!

It was a serious matter that Sima Chunfeng, who was the center of the work of the State Council Academy, the leader, and the present and future of the Academy itself, had to briefly go to the Wulin Alliance to report the situation.

The entire operation of the university will be in turmoil due to administrative chaos caused by Sima-lang's absence and the inexperience of the academic faculty.

Of course, this was Sima Chunfeng's one-sided claim.

Qing nodded.

``Yeah, yeah. If that’s what Sima-lang said, then that’s what it must be. Wow, it’s so annoying.''

``Hahaha, of course. What Sima-lang said was the absolute truth. I thought Heavenly Blossom Sword would think the same way?''

"hmm."

Where on earth does this endless, passionate self-love and confidence come from?

"Then I guess I can just go and sleep. Have a good trip. And take care, just in case."

Anyway, the Wulin Alliance was right in front of us, so it wouldn't be a long trip, right?

This was also a surprising change in perception, as it could be said that the Qing had now become a Zhongyuan citizen.

It was approximately 500 li from the school to the Wulin Alliance.

In terms of the Qing hometown, it was the distance from Incheon City (Incheon Manse), the capital of the homeland and the birthplace of mankind, considered the best city in the world by 8 billion people, to the East Sea on the other side.

But for the people of Zhongyuan, 500 li was literally a distance that can be reached by nose if you fall down.

Anyway, it's not like you're crossing the city border from Hanam to Hanam, and it's a flat road with not even the usual hills of the Hanam Plains, and it's even the headquarters of the Jeongpa martial arts community, so it's extremely rare (though not impossible) to encounter bandits and demons, so it's a safe road, isn't it?

"Heavenly Blossom Sword? Were you really joking about sharing the same bed?"

"Huh? This isn't a joke. We're at that level now, aren't we? We're best friends sharing a bed, aren't we?"

``Ahem. That’s about it… close friends…''

Sima Chunfeng's lips were somehow curved, somewhere between joy and shame, and he couldn't meet her eyes for no reason, so he looked at the patterns on the floor and wall.

Because of that, I couldn't look at Qing's face.

Qing's eyes were narrow and sinister, so he did not notice the gaze that was staring at the heavy wisdom pouch of Jinang Hyeonhwa, or the bright red tongue that was seductively licking his lips.

In the past, the expression on the face of a woman named Mo Nan-ah, the daughter of Mr. Dang Mo, must have been exactly like this.

Anyway.

And another victim.

"no."

``Huh.'' ``Ouch.''

The two little ones' eyes widened, and they were so shocked that they just stared blankly up with their eyes shaking.

It was Ciyu and Zhuge Xiang who came to see their father/companion whom they hadn't seen in three days after finishing their daily schedule, which was somewhere in between boys' class and boys' play.

As usual, he came running with a smile, but it wasn't the usual soft and comfortable embrace of Qing, or the round, smooth skin of her cheeks that was rubbing against her.

Only Xue Iri's stern expression blocks the way.

So, the two little kids were just fidgeting and looking around to see if they have done something wrong.

What were Qing's feelings when he sees that sight?

Of course, it's very cute.

The way the little ones were crouching and looking around was because Qing was the type of naughty uncle who was originally cute to children.

"Young Lady Ximen iss badly injured. For the time being, no hugging or jumping on her was allowed."

``Gasp.'' ``Gasp.''

In an instant, four large, moist eyes turned towards Qing.

``Are you hurt? Does it hurt a lot?''

"Gege, are you okay? What should we do? If you can't even hold us…"

"Hey. No. He's badly hurt, but not so bad that he can't hug our little ones."

Qing-i Keum, and then her voice cleared.

``Let’s hug just once, just once.''

Qing said this and spread both arms wide.

Ciyu and Zhuge Xiang's expressions brightened again.

And then, as if they had been waiting, two little kids came running towards them, and Qing took them in.

``Ugh!''

That was a natural result.

How could a woman with countless pieces of metal stuck in her torso handle two children's torso slams?

It must be said that it was brave of him to put the children on top of me so that they wouldn't get hurt, even though he fell down on his butt.
