\chapter{Great Instructor Ximen Qing (11)}

Of course, no matter how pitiful or admirable Wan Talu is, there should be no favoritism.

Although it was said that no finger can be bitten without causing pain, there were definitely fingers that hurt less.

In many anecdotes and tales, aren't there resolutions to cut off one's ring finger or little finger and offer it or feed it to others?

The thumb, index finger, and middle finger were superior to the other three fingers, and this was a clear fact proven by history, legends, and the left-hand law.

If the school schedule continues, I'm not sure about the future, but I don't want to show that I care about anyone especially anymore.

So, Qingdo, just think to yourself.

I saw it again. They say a person's true nature was revealed in difficult and challenging times. Maybe I never had the chance to become a better person.

But, what was it? The atmosphere?

``Thank you, Instructor!''

``Thank you for teaching me, Instructor!''

``Instructor! May I ask you to show me which path was smoother between the ``Chukcheoreokchakcheok'' and the ``Chakcheoreokchakcheok''?

For reference, Buungbangbung was a medium sword, Wwaeakssapjjang was a quick sword, and Cheoeokchakcheok was a strong, medium, and weak sword. It was a really easy-to-understand expression.

Anyway, somehow the principal's atmosphere was hot.

Of course, the academic atmosphere was very good before.

Of course, they were not all brought in by force, but were selected with a strong desire to learn, so they were not negligent but rather diligent.

``Thank you!!''

``Indeed! I will try my best!!''

First of all, didn't the vocal volume increase significantly?

Suddenly, the military discipline was at its peak, and they were passionate disciples?

Are you feeling motivated after going out?

But the next day too.

``Instructor!! Hello!! Did you enjoy your meal!!''

``Thank you again today!!''

And the next day too.

``Instructor!! Good!! Morning!!''

``See you tomorrow!!''

The next day, and the next day.

I thought things would return to normal after a few days, but somehow the military discipline doesn't go away.

If other people heard me, they'd think I was really good at catching kids. Well, they're all dream trees in their own right, so their voices were really loud.

Was it just a voice?

As we gradually became closer, the friendly terms like ``you punk'' and ``you little punk'' disappeared and we started calling each other ``hyung'' and ``dongsaeng''.

Those guys who used to just sit down and do nothing when they were tired and even lie down, now sit cross-legged and do yoga to relieve their fatigue in a dignified manner.

Who am I? A swordsman. Just now—

Even?

``The instructor is here!''

``Have you had dinner?''

Qing couldn't hide her surprise.

It was a surprise visit in the middle of the night, a surprise visit to the dormitory that was in charge of the basics of 'I won't touch you if you just stick to the basics, just do the basics, just the basics'.

It's basic, but what in the world was more difficult to stick to than basics?

So, when Qing made a surprise attack and opened the door with a loud bang, the first thing that came out was the smell of a bachelor who was about to lose his nose, along with the stale sweat of his roughly collected laundry, and an indescribable scent of men.

But, how?

Sniff sniff. Qing sniffs.

Except for the inevitable parts of a men's space, um, it's clean, right?

The room was clean, and there were hardly any cases of people lying around with their shirts off like before, then suddenly covering their bodies.

Of course, there were always exceptions.

As soon as I opened the door, there were several long strings hanging horizontally, as if they had been picked up somewhere, and all kinds of underwear were lined up.

It was like a Christmas decoration or a national flag on a festival day in my hometown, so, come to think of it, maybe there wasn't a place to hang my underwear separately.

Oh, Che Yaohong Guan Do, I didn't know because he always wore a thick hopi coat, but he was actually amazing.

But whenever I look, the women's dormitory was always the most messed up…

Anyway, the swordsmanship hall was full of military discipline.

I thought it was just a side effect of going out, so I thought it would go away after a day or two, but it keeps going on and on, so what was it?

Did they turn around as a group?

And after much thought, Qing came to a conclusion about this desirable phenomenon.

This was so cool, thanks to the new Wan Talu.

Qing was an intellectual who graduated from a university in his hometown and was a leading expert in psychology who completed the course ‘Life-Changing Liberal Arts Psychology.’

And through observation and analysis that he carried out as if breathing through social life, he was also the embodiment of harmony that naturally blended into any group, like water in water or alcohol in alcohol.

In the eyes of this authority on human understanding, it has become less rustic.

People tend to avoid doing things that were out of place in a group rather than doing cool things that were defined by their roles in the group.

So, it's the same principle as your attitude during class.

How about being loved by your teacher in class and achieving great personal success?

Well, everyone knew that.

Just ask questions whenever you don't understand something, participate actively in class, and focus on your studies.

As seen in many media, this was also a very cool image of a strong student and a passionate student.

But the vast majority of students don't do that, because it's incredibly unsophisticated.

Even if I do that, I'll just be evaluated as, "That kid was just trying to look good to the teacher, why was he making a fuss, what an unlucky kid, etc."

In the military, sincerity was looked down upon, everyone tries to be as relaxed as possible.

Even in my later jobs, it was the same.

Passionate coworkers were often called nuisances, company stooges, or even social outcasts.

Of course, there were a few normal groups, and in these groups, there was an atmosphere where showing off one's normal coolness was considered a non-tacky act.

And since Wan Talu kept making a fuss, I wonder if that kind of atmosphere has somehow spread to my swordsmanship too.

Even the exquisite one, because the original dog's jaw was so ugly.

No matter how much trouble he made, he probably didn't get much backlash because of the so-called 'fairy effect', where people said that Shin Wan Taluo and Shin Dalro were better than the previous Gaebaldagwi and were much more like fairies.

Of course, this atmosphere was usually the capacity of the group leader.

Qing also heard this part, saying that it was because the leader's leadership was important.

Hmm? So, what was it? It's all thanks to me?

Has the Transcendent Flower Sutra, the Super Flower Sutra, and the Super Word Sword once again made a great contribution to the martial arts world?

Heavenly Blossom Sword, were you saying that even the instructor was the strongest?

Apart from that, the work of the thanksgiving has become a little more, no, a lot more arduous.

Because of the countless requests for handshakes, no, countless requests for consultations.

The cause was the constant praise of Instructor Ximen by Wan Talu.

``Since Instructor Ximen has severely reprimanded me and has shown genuine concern for me and cared for me as a lacking disciple, how could I not renew my resolve?''

``Instructor Ximen has shown me the right path in life. It was the grace of a teacher who guides a small person by pointing out the right path. It has been deeply engraved in Soje’s heart. Each sentence was a golden and jade piece with a noble fragrance, truly moving. To Soje’s shame, I ended up shedding hot tears.''

"Ah, you mean the most beautiful woman in the world? Sword flower? Ice flower? What were you talking about? Of course, who else but Instructor Ximen could dare to talk about the most beautiful woman in the world? Oh my. Brother Jang, of course there were famous beauties in the martial arts world, and everyone's tastes were different, so some may be more beautiful in appearance, but was there anyone other than Instructor Ximen who has the same level of discipline, character, dignity, and noble martial arts skills, and was also internally perfect?"

"Brother Yoo, you've been feeling down lately. Oh, dear, I didn't realize it. However, I'm still young and don't know much, so perhaps you should ask Instructor Ximen for advice?"

``Instructor Ximen……''

``If you were Instructor Ximen……''

``This must also be the grace of Instructor Ximen.''

Since it was a Wan Talu story that ended with the praise of the instructor Ximen ten times a day, I respect the rising action, turning point, and climax of the story. I couldn't help but ask for this just out of curiosity about what kind of consultation it was.

Using his injury as an excuse, he left the instructor training of Geom Ok-gyun to Nan-gong Shin-jae.

When you think you can enjoy some rest and relaxation, you can't help but be flustered by the sudden influx of people coming to you with concerns.

However, I couldn't refuse using the excuse of recuperation because I felt a useless sense of responsibility.

``Instructor Ximen, there’s something I’d like to discuss with you. If you don’t mind…''

``It doesn’t matter to me, but since there were quite a few people waiting, if you don’t mind waiting a few days, I’ll write you a number.''

``Huh? Even the number tag? Number twenty-two? Oh, but what’s the writing on it? Oh, oh, oh my.''

To prevent counterfeiting of the number, it was written in difficult characters, so the eyes of the officials looking at the note with the number 22 written on it trembled violently.

Because he was a government official who could read and write.

No, what kind of writing was this powerful and neat, with the front and back teeth matching perfectly as if they were glued together? Isn't this the work of a master who has perfectly honed his own style?

How can this be? Even Instructor Ximen was the best at writing!

Even the written word alone was a precious treasure worthy of long-term adoration. How could you give away such a precious thing so lightly, let alone consult with someone else?

So, the government was worried, so they were going to get some advice first, and then they were going to get some more advice, so they were going to ask if there were any other concerns that they should get advice on.

Even before the consultation, the client's satisfaction level was already through the roof.

This also meant that Qing's evening rest was in serious danger.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Do you know the law of conservation of dogs?

This refers to the very mysterious phenomenon where the number of dogs in a group remains constant.

For example, let's say your boss, coworker, or subordinate was a total jerk who always asks you to quit.

If that bastard were to vanish for some reason—quitting, getting fired, or maybe someone finally acting on their fantasy of stabbing him with a knife—I'd be incredibly happy, of course.

But that joy would be short-lived. Someone else, who seemed perfectly normal until then, would take that bastard's throne and start acting like a complete asshole.

In other words, when a dog leaves a group, a new dog was sure to appear to fill that spot, so the number of dogs remains constant.

This was a scientifically proven fact.

Observations of ants show that about one-third of them just play.

What if we just get rid of all those ants?

Surprisingly, among the ants that had been working hard, another 30% started playing, saying, 'It's finally my turn.'

And so it was with people: the moment a bastard's seat becomes vacant, another bastard inevitably emerges, awakening to the realization that now was the time for them to take on the bastard's duties.

Of course, some people would argue that that's not true, that there were no such assholes in my workplace.

If you really feel that way, you may need to reflect on your own behavior and have an honest conversation with your colleagues.

The swordsman was not free from the law of the bastards either.

Wan Talu said, ‘I will stop being an asshole’ and became a polite young man armed with inhuman sincerity, leaving the position of the asshole of a swordsman empty.

And now a new bastard has appeared.

But, this time, a terrible exchange rate was created with three people, one son of a bitch, disappearing and three more being added.

These three bastards were the ones whose skills suddenly improved after going out.

On our last outing, we were all huddled together in a cramped, palm-sized room in a hot summer day, sweating with our shirts off.

The three servants of the Blood Cult Infiltration Unit, who were forced to do odd jobs due to their lack of skills and intelligence, but who passed the exam without much luck because their bad karma was still low.