\chapter{Great Instructor Ximen Qing (9)}

A real way to remove a piece of metal stuck in your body.

Anyone who follows this will be able to remove the embedded fragments as easily as eating soft noodles.

The materials required were as follows:

A tool for removing metal pieces. Tongs, etc.

One or more people with metal fragments embedded in their bodies.

If you don't have such a person, you can make one yourself.

If you procure the materials directly, you must be careful as infection may cause high fever and decay of the affected area due to the sanitary conditions in the Zhongyuan.

Afterwards, remove the material from the costume and lay it down.

Naturally, the refund will be placed on top.

Qing lies down on the floor naked.

It would be comfortable to lie down on the bed, but I was afraid I might get bloody, so I laid down a towel and lay down on the floor.

However, it was not so surprising that Qing was lying naked.

A common sight, isn't this the behavior we've been doing up until now, even if it's not the removal of the embedded pieces like now?

I tend to sleep naked, so it was a strange habit I picked up during Ximen Surin's self-defense class.

anyway.

It was said that the face was the key to beauty, whether for a man or a woman.

But even excluding the face, Qing's naked body was dazzling.

The proportions of the long legs coming from the unusually high hips, the slender waist drawing a dramatic curve from the large hips, and the massive sculpture above it were the finishing touches to the figure.

Second removal of the iron shard.

Gently stroke the affected area with your fingertips to find the piece of metal.

Qing gently strokes my stomach.

Although the abdomen was built with perennial abs that were as strong as a human, it was smooth on the outside, with only dazzling white skin without a single blemish.

Murong Zhuji-hee's breathing became somewhat ragged as she watched the scene.

Somehow, my pupils dilated and a blush rose on my cheeks, and I gulped as I looked at that obscene body again.

Chen Changming and Xue Iri look at him with displeased expressions and give Murong Ju-hee a displeased look.

However, after the ordeal, Murong Zhuji maintained a gentle and yielding attitude.

So, the two women didn't bother to look at Murong Zhuji and criticize her by saying things like, "Your expression was very impure," or "You should muffle the sound of your heartbeat."

This could be said to be a passage that shows how important one's usual attitude is.

And remove the iron pieces, three.

Pull out.

Qing pulls out the piece of iron with a cheerful attitude.

Qing was a master of the Hwagyeong and also possesses evil powers that surpass humans, so he does not need to rely on tools such as tongs.

``Gasp.'' ``Gasp.'' ``Ouch.''

Those who were watching could not help but be surprised.

Suddenly, the atmosphere changed to a scene of self-harm.

The red blood that had risen from the iron shard that had pierced through the flesh began to drip down the road.

"Write. See? This was how you do it."

``No, what? You’re saying you’re going to pick someone so ignorantly?''

Chen Changming frowns as he wipes the blood with a towel.

"As your muscles heal, they'll gradually fall out, but they still have to be pulled out eventually, right? So, pull out what you can, and the ones that aren't yet there will pop out over time, so just pull them out then."

You could do it alone, but you'd need a few iron shards embedded in your muscles.

So, if we all pull out the Jincheonroe fragments together and pull them out again, and pull out the fragments that haven't come out yet tomorrow and pull out the sand, we'll be able to remove them all.

``Me too. Me too.''

"Oh, even Ciyu wants to treat Daddy? Wow, our Ciyu was such a filial daughter. If she keeps up like this, she might end up with a monument erected to her filial daughter. Oh, and Wang Geon was here."

Qing tapped his side, then lightly scratched his young cheek with his fingernail.

Through the small, cracked skin, a dark, jagged fragment of Jincheonroe was peeking out.

Ciyu holds out her tongs with an excited look.

Then grab the fragment and use it, it hurts a little.

Tick! Tick! The sound of forceps clashing.

Because the place where the fragment was embedded was the blue muscle.

It was the strongest muscle in human history, strong enough to spit out a foreign substance that had been stuck in the body with the force of a ten-year-old child!

``Use it.''

Even though countless pieces were stuck inside the muscles, it was a blue that walks, eats, and lies down normally, so it doesn't hurt terribly if you tap one of them.

The human body responds to pain by shrinking, so the muscles clenching the shrapnel twitched, and the mouth groaned and groaned.

Ciyu flinched, and then tick, tick. Tick tick tick.

``Does it hurt? Does it hurt?''

"Ciyu'er? Aren't you a little excited? Our Ciyu'er, you're such a filial son of a bitch. We should erect a monument to filial piety at the entrance to the school building tomorrow."

He suddenly shrunk to a crawl.

Well, it's already too late. Killing was fun, but you still have to be careful about who you kill…

Well, I didn't expect anything from Ciyu in the first place.

If it seemed like it would be pulled out to that extent, the doctors would have already removed it and left it behind. Since that wasn't possible, they would have pulled out what they could, applied medicine, wrapped it up, and covered it up.

"Okay, see? You have to use your internal energy to pull it out. If you put it on a pair of tongs, it's a tongs device. Anyway, leave the ones that haven't come out yet, and only pull out the ones that were sharp- AAAH!"

Qing screamed in excruciating pain.

Then, as if to show off, Chen Changming lifts up the large fragment caught in the tongs.

``Oh. It’s really big. I think I’m the biggest.''

"Changming'er? This isn't a game about who can pull out the biggest lump— ugh."

Then, Xue Iri stretches out the tongs with the fragments attached and compares them with Chen Changming's.

Although similar, the fragment of Jinjangmyeong was subtly larger, so a subtle shadow appears between his eyebrows as if he doesn't like it.

``Uh guys?''

``It's a good opportunity to change her bad habits now.''

Xue Iri nodded.

Wasn't that the girl who embraced Jincheon-roe?

Even pulling out the shrapnel embedded in my body was like playing a game, so I guess it doesn't hurt much yet. I think I should be really hurt so that this kind of thing doesn't happen again.

So, since the two of them have expressionless faces, they were quietly running their fingertips over the skin and tapping it with their other hand, and they were full of the momentum of wanting to completely destroy it.

Oh, this isn't it.

It was a bit different from what Qing had imagined, so it was only once or twice that he had been unable to protect himself.

However, we can take into consideration the aftereffects of the life-or-death situation and the sharp sword.

But I even went so far as to jump into the fire myself? That's why Xue Iri continues to reveal her feelings through silence, and why Chen Changming, who heard the news, feels the same way.

Qing turns to Murong Zhuji and asks for help with her eyes.

The atmosphere was getting weird, Young Lady Murong, can't you do something about it?

``Whew, Whew.''

However, Murong Zhuji just kept her face bright red and was twirling the fragments that were caught on Qing's thigh and fingertips.

``Whew, my lady, will this hurt? Or will it sting? Will it sting?''

Hmm. The condition was really bad. Did he somehow regain his memories of being kidnapped? The way he was shaking, thinking about it, seemed like he could be sensitive, but I was short-sighted—

``Oh, damn it,''

Anyway, it was the result of Qing's self-imposed actions.

Because it was the law that one had to take responsibility for one's own actions.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

During breakfast, Yang Qi, the leader of the swordsmanship training group, felt something was very off.

Something, something feels strange, empty. What was it?

Yang Qi glances at his assistants.

First of all, two people from Yanchang.

"You bastard, how can you eat so well? You've destroyed someone else's family, and yet you're so brazen, you're so shameless."

``I’m sorry, but please accept this.''

"Ugh, this piece of meat is too small. Do you think this will be enough to comfort me? Mumble, mumble."

After the noise and equipment, the avenger Hosooin, who only talks about avenging his family's enemy, and the son who came from the enemy's family's house.

The sins of a family cannot easily disappear just because it has left the house.

However, since he was Zhang Feihu, who had abandoned the comfortable path of being the leader of the Sapa faction and entered the Academy of Political Affairs, it was an issue where he could not take sides as a third party.

Personally, I think Zhang Feihu was a very dignified person, but as a first-class martial artist, he continues to take care of the noise unit, trains them, and was noticeably considerate.

So now, the noise level was just a mess, with enemies and enemies talking, but aren't they still eating the meat side dishes they're given as if it were a given?

And next to him, Sword Jade-lady, a master of swordsmanship and already a top-class instructor, was eating with a dagger, or to be exact, eating.

I heard it was part of the training, but it was unclear how much of the act of eating rice with a dagger and stabbing and stabbing and stabbing and stabbing boiled pork, which was so tender it was almost melting, was training.

Next to her was Che Yaohong, a woman wearing a tiger-skin coat over her training uniform, who doesn't shed a single drop of sweat even when the heat was rising.

But the person watching was even hotter, so how on earth did he wear that thick hoodie?

And the Sichuan nobleman, Wan Talu-

\textit{Oh, I see.}

Yang Qi realized the cause of the discomfort.

He didn't hear all the colorful, negative comments that usually accompany meals.

\textit{What, why today? Even though it's an edible meal, it's by no means delicious.}

``Trainee Wan? Does the food suit your taste?''

"Who eat food for the taste? You need to eat well to train well. And it's not so bad that you can't eat it, Brother Yang."

A chill ran down Yang Qi's spine.

\textit{What did I just hear? Brother Yang? Why is that guy using honorifics?}

It wasn't just Yang Qi's reaction, as the sound of eating at the table suddenly stopped.

Because everyone was looking at Wan Talu with expressions like, 'What the heck did I hear?'

But Wan Talu looked calm.

And then he continued speaking very calmly without changing his expression.

"Ah. That's right. I've been reckless and disrespectful, using harsh language. I'd like to take this opportunity to apologize to you all. I'm sure you've been inconvenienced by this annoying brat's lack of discipline."

"You, you piece of shit. Did you eat something wrong? You're creeping me, so why don't you just throw it away and go back to whining like you always do?"

"I've also been rude to you, Sister Che. Even if you call me that, it's only just."

Flames blazed over Che Yaohong's robe.

Then she started rubbing her arms wildly while making a fuss.

"Hey kid, what are you doing? Who are you? Why are you sitting there wearing Wan Talu's face? Ha, no, so what? I like this one better."

Despite Che Yaohong's continued sarcasm, Wan Talu remained calm.

However, that was why I am unlucky.

I also think that even a polite attitude can be unlucky.

``Uh, Trainee Wan?''

``Please be informal. Aren’t you older than me?''

``Ahem, um, yeah, Little Brother, did you, did you have any change of heart or something?''

Then, as if he had been waiting, Wan Talu answered.

"When this Little Brother went on last outing, Instructor Ximen gave me advice, and with the love of a teacher, she encouraged me. This Little Brother was deeply enlightened, and I realized how indulgent and childish I had been. I resolved to become an adult from now on. That's all."

The crew members looked at each other.

\textit{What kind of counseling did he received to completely change himself as a person?}

\textit{Even if he gets hit like that, that's all. After a while, when the pain goes away, he continues to bite.}

\textit{Is it possible that she's taken out Wan Talu's soul and put in someone else's?}

\textit{How on earth can you make this correction, not correction, but something closer to a complete remodel?}

Yes, the crew members blinked their eyes.
