\chapter{Great Instructor Ximen Qing (13)}

Gu has been considered one of the most powerful sorcery since ancient times, but despite its high notoriety, it was also a relatively simple sorcery.

After gathering a bunch of poisonous creatures, just gather them in one place and gently say, "From now on, kill each other."

Among them, the one that survived until the end was the strongest poison, the birth of Go.

Because it was so easy, in the distant past, when sorcery was more mainstream than martial arts, the country would crack down on it and ban it, so if you were caught making it, it was considered the worst sin, with the entire clan being wiped out without question.

The current Zhongyuan was an era where sorcery was half-assed and half-powerful, so even if you say it's lonely, most people don't believe it.

Of course, the method of making it was simple, but the making itself was extremely difficult and requires extremely advanced technology.

If you think about it logically, no matter how poisonous a creature is, would it be okay to eat someone else's poison?

So, even if you just gather poisons in a jar and start a fight, all you get was the corpse that was the poison, and all you lose was gold and time.

So, the birth of the parasitic salamander, the blood-sucking one, was a madman's investment, melting down thousands of gold crowns, and the creation of an unprecedented, mysterious species, a miracle, completed with the obsession of highly developed sorcery.

And it was a liquor bottle located a few generations below the finished product's genealogy.

Eating the creatures we encounter was the answer our ancestors reached to survive in that terrible crucible, an instinct engraved in our species.

Well, this guy's drinking like a slob, he just eats it raw without even chewing. Well, I guess that's to be expected since he doesn't seem to have any teeth.

He's a drunkard who would dare to bite you if you poked him, but he didn't care.

If I were to roughly feel around, it was a bottle of alcohol that first bit the head and then pushed it in little by little by giving it a rebound.

There was a clear weight difference between the big drunk who has been diligently sucking poison and the newly awakened drunk, but in the end, it was an amazing predation that occurs despite the fact that there was not that much of a difference.

So, the glass disappeared and became the specialty of the bottle, but, well, the glass will live on as the blood, flesh, and poison of the bottle, so I guess it's a happy ending in its own way.

I guess it's because Qingdo was a pet parasite that I didn't even have time to get attached to.

I have one, but I don't need two.

The bottle swallowed a large prey that was more than half the size of its body.

So, wouldn't it be nice to have a plump body and lie down on your back?

Since pet parasites and their owners were exactly the same, you could say that parasites were like beasts, and conversely, you could say that beasts were like parasites.

That was the moment.

… … Oing!?

The condition of the alcohol bottle is… …!

I thought something was moving, but it turned out that all four legs were stuck in there. Oh, they weren't stuck in there, they were buried. What was it? A cocoon? What kind of salamander goes into a cocoon? Or not? Were salamanders always like that?

Of course, Qing didn't know anything about the ecology of salamanders, so I guess it was because they were so precious and unique that they were considered natural monuments or something.

Is it a natural monument? A protected species? Some kind of cultural asset? Whatever, it feels something like that.

It doesn't seem to be a problem, and I doubt it will turn into a pterosaur or something when it wakes up later, so I'll just leave it to grow on its own.

It's a pet parasite that can be melted down with internal energy at any time, so it's a shame about the free alcohol (it feels similar), but I'll see if I can join you when I see it.

If we have more than six legs, then from then on we will not be able to be together.

Rather, um, what the hell do I do with this kid?

How dare you gift this body with a pet parasite?

The terrible things I've experienced because of that.

First, the damaged, swollen, and painful Qi meridians caused by the chaos of the Heavenly Demon True Qi were calmed and settled down comfortably due to the strong medicinal properties.

Not only that, a mysterious energy of unknown origin welled up in my dantian, and my internal energy even increased.

Even the bottle-eater locked himself in a cocoon due to the pain and shock of the tragic cannibalism.

How dare you commit such a terrible atrocity against me, and make my bottle evolve!

I will never forgive you! I will take revenge!

… … Well, it’s a bit vague.

Is this really an attempt by Jo Gwan-do and Jo Hyeon-il to inflict loneliness on Heavenly Blossom Sword, the future and only hope of the Jeongpa martial arts world, as a member of the Blood Cult?

Or maybe he was simply asked to deliver it to Heavenly Blossom Sword in exchange for the elixir.

However, I would not have been threatened by the addiction to loneliness.

When the bottle of alcohol was used as a final poison spewing technique by the secret group, after the excruciating pain subsided, he looked puzzled as if he had no idea what had happened.

That means I've never suffered terribly from loneliness, unless you assume I'm some stupid, blackmailed idiot.

There was no way that loneliness could have been contained in the heirloom, so it was definitely not an elixir that was kept as an heirloom.

Well, isn't there a way to really nail it down, a way to make its identity clear?

Qing scratched the back of his head.

Miss, how nice it would be if you could just ask and get an answer.

Guan Dao has nothing to do with blood sects, right?

Yes, it doesn't matter.

Okay, let's work hard.

or not

Guan Dao has nothing to do with blood sects, right?

No, I am the blood cult member.

Then split in half and die.

How convenient and simple it would be.

But even if I ask, he'll deny being a blood cultist anyway, so asking him all day was pointless.

If you try to torture them, they will eventually become so pained that they will claim to be blood cultists even though they were not.

Qing continued to scratch his scalp, but at some point he stopped.

No. Why can't I ask?

A person was a person because they can communicate. If they can't communicate, were they really a person?

Just ask frankly, manly, honestly, and directly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

When Jo Hyun-il returned to his bed after finishing his school work and opened his locker, he came across a bright red note that he had never seen before.

What kind of prank was this? These days, those without talent or ability can't hide their ugly jealousy. It must be part of that. Jo Hyun-il picked up the note casually.

"I know your secret. Come to the Sword Master's warehouse by the 2nd hour. If I arrive and no one was there, your secret will be widely known."

Jo Hyun-il drops the note in a panic, then grabs it before it hits the floor and looks around frantically.

Since training had just ended and everyone was busy packing up their clothes, fortunately no one seemed to have noticed this suspicious sight.

Jo Hyun-il feels relieved for a moment, but a beat later, his heart sinks and he feels a chill.

My secret? Surely not. Surely not. It shouldn't be. If you mean you know my identity, then that means you know my identity.

Jo Hyun-il hurriedly headed outside.

Jo Hyeon-il, who discovered two other people among the officials who had just packed their clothes and were heading to the valley, calls them over in a hurry.

``What’s going on? I feel so uneasy.''

``Let’s wash up first and then talk.''

"Now was not the time to be leisurely washing yourself. Look at this."

Jo Hyun-il hands over a red note to the remaining two members of the Blood Cult trio, Bang Yun-eol and Jang Jeo-sam.

The two of them looked at the note wondering why it was like this, and their expressions also froze.

Well, according to what the three learned, the Zhongyuan people would catch anyone who was a Blood Cultist, pull out their fingernails and toenails, and then beat them and burn their skin for fun.

So, the destruction of the Zhongyuan was the only way out for our blood followers, the sacrificial lambs who have been and were being persecuted.

The commonly used mental armament, or brainwashing.

If you were born into a closed society and everyone was taught that way and it becomes common sense, no matter how smart you are, you can't help but believe it.

And, in fact, it's not that wrong, it's just that there's a difference in water level.

Because when it comes to blood sects, all three groups, the people, government, and martial arts world, hate them and try to eradicate them.

``What, what was this?''

``You, how on earth did you behave like this?''

Jang Jeo-sam growls fiercely as he grabs Jo Hyeon-il by the collar.

Jo Hyun-il lowered his voice while being caught.

``No matter how much I think about it, there’s nothing I can do, but isn’t it more important to figure out what to do now rather than blaming others?''

Jang Jeo-sam then roughly grabs the hand that was holding his collar and lets go of his hand, which had been disrupting his daily life.

Jo Hyun-il tugged at my clothes, straightened them again, and then opened his mouth.

"We have to make a decision right now. Should we abort the mission and flee immediately, or should the three of us stick together and hunt him down?"

``Isn’t it just you who has to run away?''

"How do you even know if I know your true identity? If I were to run away alone, and you saw me running away, you'd think you'd have to catch me first?"

Their expressions became serious.

After listening, I realized that it wasn't just Jo Hyun-il's problem.

The timid Bang Yun-eol stamps his feet.

"Then how? No, this isn't the time. We need to get out of this Zhongyuan den right now—"

"No. If you run away, the mission will fail. And didn't you hear when the leader distributed the elixir? It was a elixir made by the Ma-Hwang and the Venerable One themselves. Even with such grace, you still fail the mission? I doubt you'll make it out safely."

``Well then, what should we do?''

"If I'm going to die anyway, I'd rather kill this guy—whoever he is—and silence him. That's the only way for us to survive, for our family to survive."

Then, the eyes of the three officials show determination.

To live, to survive.

And that night.

The moon's position was still around the end of the midnight hour and the beginning of the ox hour, so there was still plenty of time left until the promised time.

Jo Hyun-il's expression was unpleasant.

What a cunning trick this is.

I'm not asking you to come out at midnight because I'll be waiting.

He said he would come at midnight, so come out first and wait for me. If I wasn't there when he got there, he would immediately reveal the secret.

Because of this, the three of them couldn't move together carelessly, so they must have been waiting for a while to see if he would do something and then show up at that moment.

``Well then, please don’t be late.''

The two officials nodded silently.

Isn't there only one way?

First, Jo Hyun-il heads to the warehouse first, and only after midnight does the remaining two move to attack.

If there were a group of blackmailers watching, it would all be in vain, but if I were going to die anyway, I had no choice but to choose the plan with the highest probability.

So, Jo Hyeon-il was the first to sneak across the school building at night.

Very cautiously and secretly, in case we ran into any of the school security guards.

Of course, it was Jo Hyun-il's own thought.

To anyone who saw him, he looked like a very suspicious guy, constantly nervously looking around and trying to figure out whether he was sneaking or not.

Since this was how we use our bodies, we cannot observe our own bodies as if they were someone else's, so wouldn't the postures, movements, and actions that we feel and intend be seen as funny by others?

So, the infiltration continues in a very suspicious and clumsy manner, with the only experience being stealing potatoes from the kitchen.

And finally, I reached the warehouse and gently pulled open the closed warehouse door-

Squeak.

At the sound of the wooden hinges twisting, Jo Hyun-il jumps up like a cat splashed with water.

It's cute when a cat does it, but it's quite ugly and shabby when a dark-skinned man does it.

Finally, I carefully squeezed my body into the gap that had opened -

``Huh. Are you finally coming?''

Jo Hyun-il was startled by the loud voice and gasps, falling hard while gasping for breath.

He immediately jumped up and drew his sword, but that didn't mean it wasn't embarrassing.

"Tsk tsk. What a worthless bastard. Are you saying our school was so short on talent? You punk, when you see an elder, you don't even greet them first. Who taught you to swing your sword first?"

"yes?"

Jo Hyun-il asked stupidly.

Because the blackmailer's words were completely unexpected.

Is this your school? Is this your elder?

Jo Hyun-il was in a state of confusion.

The mysterious assailant raises my arm.

Then, a menacing starlight emerges. A self-luminous, bluish-green energy, a pure white demonic hand made of energy, a gigantic hand with a strangely twisted shape and a strangely beautiful corner, rises high above.

Magical number!

Harmony, or the idea used by the White Hand Witches in the mouth, was a symbol of the White Hand Witches.