\chapter{Great Instructor Ximen Qing (2)}

Qing looked at Tai Lingfan.

She looked at the astonishing sight of him holding onto the iron bars and sticking his head out, calling out to his subordinate with an expression of infinite sorrow.

\textit{Why a man who knows how to cherish and love his subordinates be so ruthless to others?}

\textit{He exploded a fire bomb to save his life, and he didn't hesitate to cut open an innocent person's stomach and sacrificed her.}

\textit{It's really funny how he keeps screaming in front of his subordinate's miserable state.}

"Why on earth, why are you doing this? What kind of grudge do you have?"

"I could ask the same question. Why on earth would you do such a thing? Heaven-shaking Thunder Bomb? If that bomb had exploded, how many people would have died? Someone's son, daughter, husband, wife, father, mother, friend—do you think the grief they all feel would be any less than the grief you're feeling right now?"

"Hehe, then what about you? My subordinates are also someone's-"

Qing immediately cut off the conversation.

"That's not true. Your subordinates aren't human. Aren't they people who set fire to the inn just to catch a single, unskilled punk?"

``It’s an Imperial Edict! An Imperial Edict!! Don’t you know what that means? I’m carrying out the Emperor’s orders!!''

"What the heck, the Emperor ordered you to set fire to the inn and throw firebombs into the crowd? Cut open the bellies of the women who were leaving and threw them aside, and then ran away to save your own lives?"

"That, that's what it means!? The Emperor's command is absolute! I will apologize to His Majesty for harming his people, and it's not your place to meddle in anything!"

``Wow, wow. No, what.''

Qing's mouth was once again blocked.

But Tai Lingfan was proud.

After all, the Emperor was the master of all under Heaven.

He was the master of all the land and of everything that existed on it.

Every blade of grass and every wild flower on the roadside were the property of the emperor, and everything with two legs or four legs were also the property of the emperor.

So what's so wrong with destroying some of that property to carry out the Emperor's orders?

Qing realized anew the primitiveness of this ancient Zhongyuan.

\textit{Come to think of it, this is Zhongyuan's natural state.}

\textit{Well, what's the point of saying more?}

Qing grabbed Jang Cheon-ho's hair.

The head that comes with it was still attached, and the wind blowing from the hole under the Adam's apple was noisy with the sound of boiling blood.

"Jang Cheon-ho, you have nothing to say? Okay. Would you like to say something about this?"

Qing covered Jang Cheon-ho's windpipe with his hand.

Thanks to this, the air that extended through the vocal cords was formed and comes out as human speech.

``Oh, please, please, please, ah!''

Only then did Tai Lingfan understood Jang Cheonho's condition.

He was in a state where he could not make a sound because there was a hole in his windpipe, but he had been screaming incessantly, begging for death.

Unlike the torso which trembled with agitation, the limbs hung down and sway with the weight of their flesh and blood.

It was a heavy sway, like a lump of flesh that was flailing without bones.

``You bitch!!!''

The sound of Tai Lingfan's voice was loud and clear.

Of course, Qing was just happy.

\textit{If you get angry, you lose, and, um, I win?}

``What the hell are you doing to Jang Cheon-ho! Jang Gang-bang! Come to your senses, just a little longer, hold on just a little longer, I, aaaah! Open this! Open it!''

Tai Lingfan held onto the iron bars and shaked it.

Without the help of Inner Qi, he couldn't even shake a single iron bar, but since he was out of his mind, only his body was shaken instead of the iron bar.

"No, what's holding out for? And what are you going to do if you open the bars? Are you some kind of god? How are you going to fix it when the bones are shattered into thousands of pieces? It's easy to break it, but hard to put it back together."

"You!!"

"Hey, don't look at me like that. You make me look like I did something really bad. I just crushed some limbs, pulled out some fingernails, and scraped them against the wall. Oh, and by scraping against the wall, I mean, something like that."

Qing held out Jang Cheon-ho as if to show him.

Unlike his somewhat intact thumb, she gently shook his four fingers, each one missed a phalanx, and then made a motion of gently grinding them on a grater by holding the ends.

``How, how could someone wear human skin and do something like this! How, how……!''

"Human skin? Ah, right. Well said. Mencius said, 'If a child was about to drown, you should try to stop him.' It's not because you want to impress their parents, or because you want to save someone and make a name for yourself, or because you dislike the sound of that child's drowning screams. Do you understand what I mean?"

The words that Qing liked the most while studying Confucianism were Mencius's test of human qualifications.

"If you don't have compassion, you're not human. If you don't have shame, you're not human. If you don't have modesty, you're not human. If you don't have the desire to discern right from wrong, you're not human."

You may think that it was very difficult to be human, but that was why Mencius said that it was the heart, meaning that you must have a guilty conscience when you do something wrong.

"So, when you see those who push a child into a well instead of saving him, are they human? Is someone who harms innocent civilians for their own self-preservation a human, or is he something disguised as a human?"

``That’s what you’re going to say-''

"You're even a government official, aren't you? The one who should be diligently managing the riverbed was actually leading the way, mutilating the people. Wow, seriously. You're not human."

Mencius said that human goodness was as natural as water.

Just as it was natural for water to flow downward, it was also natural for people to be good.

But does water always flow downward?

If struck, a column of water can rise up to the top of a person's head, and if the water was blocked and a dam was built, it can rise to the top of a mountain and collect.

This was because the environment does not allow water to flow downward.

When a river was diverted, the water also bent and flowed, and when a river was blocked, the water stagnated and rose.

That was why governing a country was like this.

It was the work of maintaining human nature and goodness by cutting through crooked places, clearing blockages, and digging shallow places so that it can flow smoothly and quietly.

So, if the government could not protect the goodness of people, then they were a being that prevented water from flowing downwards.

Is such a being really necessary?

No, that's not necessary. They're beasts, not humans, so kill them.

Revolution, that's the revolution angle.

This was Mencius's theory of revolution, and this was what Qing was talking about.

It was also something that Tai Lingfan couldn't help but shout out.

"Treason, treason! You bitch, such outrageous talk—"

"Right, is this thing really a person? I'm curious, so let's take a look. You never know. If we peel off the skin on its face, some kind of beast might come out."

``What?''

For a moment, Tai Lingfan couldn't understand what she meant.

The pure white hand of Qing, which was holding Jang Cheon-ho's lower chin, and the cool white fingers that shone through the sunlight, made him immediately understand what hse meant.

``Wait, wait! Stop! Stop it!''

Qing cut the area under Jang Cheon-ho's chin and slowly peeled off the skin attached to it.

Jang Cheon-ho's torso bounced and his head shook, but the skin was tightly coated with oil on top of his muscles, so there was no mishap of the skin being torn in the process.

Qing grabbed a large piece of crown of head skin with hair attached and threw it at Tai Lingfan.

"See? I said I'd make you beg me to kill you, and I will keep my words. That's the beautiful virtue of doing your best in your assigned role and always keeping your word. So, you have only two choices: either tell me everything you know and die a painful death, or keep silent and die a painful death."

If Tai Lingfan's mind had been a little more sane, he would have seriously questioned whether there was any reason to reveal what he knew if he was going to die painfully either way.

But once the face of a beloved subordinate was in his hands, it was not easy for a person to maintain their sanity.

``You, you bitch……!''

``Pfft!! Pfft!!''

The curses that were about to burst out were stopped by Qing who kicked the iron bars.

Thanks to that, Tai Lingfan was speechless and had his mouth wide open, and Qing raised her index finger and started waving it left and right.

"You want to scream? It's going to be noisy, so I'll step out for a moment. Are you going to bite your tongue or attempt suicide? You should think about the family you leave behind. You don't want your entire family to be slaughtered."

Qing spitted out what she wanted to say and then naturally head out.

``Well, I’ll see you in three weeks. No, three weeks is too long. I’ll see you in a day.''

As Qing said this, the iron door slammed shut.

The remaining Tai Lingfan finally came to his senses, and a loud roar of "Eaaaah!!!!" filled the tightly packed brain prison and resonated loudly.

If you've heard the sound, you'll be amazed at how powerful it is.

Qing had already gone outside and closed the door, so he could only slightly admire the faint sound of old people beyond the iron gate.

\textit{Wow, this soundproofing is no joke.}

\textit{Isn't it like you can't even breathe?}

\textit{If you leave him alone, won't he just suffocate and stuff?}

\textit{It was fun when I was enjoying it, but it was really hard to clean up.}

\textit{Well, it's fun to be a villain and torment someone while they're alive, but after they're dead, they're just a piece of meat that can't be eaten, dirty and disgusting, ugh.}

\textit{But what I find dirty and disgusting is the same for others, and if I don't clean it up, who will?}

Qing when from room to room, collecting corpses.

The remains of the shattered heads were swept into sacks, and the headless torsos were individually wrapped in straw mats, tied tightly together, and packed.

``Ah.''

Qing frowned in pain.

The deeply embedded fragments were left in place for the time being, and medicine was applied and a bandage was wrapped, so it was natural that it would hurt if force was applied.

\textit{But it's okay if I stay still.}

\textit{No, it's not okay. Every time I take a breath, a sharp pain surges here and there. It's like scratching a mosquito bite and peeling off a scab. It hurts, but it's also refreshing. So, in a way, it's not that bad.}

\textit{But, um, is this right?}

\textit{Is this the kind of reaction someone would have with countless metal shards embedded in their torso and thighs?}

\textit{Even after countless shards of iron were driven into the wound, there was no fever or festering, not even the usual pus. The Blood Poisoner's constitution didn't get worse or infected. What else could that be? An immune response? Isn't that different?}

\textit{Of course, since it is a magical body, it is not in the realm of logical causality.}

\textit{If you recover well from a full body fracture or muscle tear and were lucky, you can probably recover.}

\textit{But this is Zhongyuan, a primitive era where people could die from even a simple scratch if they were unlucky.}

\textit{Hmm, I hope they all don't think it's weird, but should I think of excuses? Well, it's a bit weird to to say it' a side effect of Divine Arts, but if I say it's because I took elixirs? Would that be acceptable?}

While thinking so deeply, Qing put down the bundle containing the heads (which was the sack of meat) and also stacked the bundle containing the bodies neatly.

\textit{At this point, I think I've given enough time.}

\textit{His head must have cooled down a bit.}

That was the moment.

A creak, the sound of a steel door creaking, were caught by her keen hearing. It seemed like the steel door on the ground level above the stairs was open.

As Qing waited for a moment, the iron door at the entrance to the warehouse opened with a creak.

And an unexpected face appears there.

``Hmm? Wan Talu Trainee?''

The Sichuan nobleman, the center of all this commotion, was the man who appeared in the underground prison.