\chapter{Great Instructor Ximen Qing (19)}

Qing's morning usually begins with a quick greeting with Ciyu. She's been sending greetings every morning, so she could be called the world's most filial daughter, but anyway.

``Aren’t you sleeping?''

``Hehehe.''

I wonder if it's a really fun pun that never gets old, but I guess that's just how kids are.

However, Ciyu's complexion was noticeably less rotten today. The original version looked so tired, but to this extent, she looked truly refreshed. Or rather, less rotten.

The dark freckles that were running down from under my eyes to my cheeks seem to have lessened a bit today.

This was why a comfortable pillow was so important.

It was a moment when Qing realized the importance of good bedding.

Sima Chunfeng quietly opens his eyes.

He woke up in a daze, his pupils dilated and his eyes were dilated, but they were so small, the size of peas, that they didn't really stand out, but he was muttering with a look that was clearly dreamy.

``Hehehe, my friend. My friend Seo Moon Qing…''

``Oh, you’re awake?''

``I haven’t been able to sleep at all, but I’m pretending to be asleep, so this was my first time seeing a close friend……''

It seems like this isn't a drunken conversation, but a dream-like conversation.

Then, suddenly, he gets startled and closes his eyes tightly.

``Sima-lang?''

``Ah, that, that’s right. It’s not like I was flustered. Ahem, sharing a bed with you, Sima-lang? It’s a timeless honor. You should have spread the word throughout the world. No, you shouldn’t have spread such rumors, should you?''

``Did you sleep well with Sima-lang too?''

Sima Chunfeng's face turns red.

"Ahem, if I may say so, I should say that the sleeping conditions of this Sima-lang weren't all that comfortable. Well, maybe for a little while, but how could it be so difficult to sleep all night? Your daughter's sleeping habits were a bit strict. Of course, it's natural for a child to seek out its mother's breast, but this Sima-lang was a sensitive sleeper. That's no use, daughter. How many years have you been enrolled this year, and you're still groping for your mother…"

``I didn’t-''

"Oh, Ciyu. Then it won't work, right? No, Sima-lang, the child might be able to touch Mommy a little. Why were you killing our child? Our Ciyu was my child? She's our child, right? Do you think it's okay for Mommy to do that?"

Qing was in a hurry.

Sima Chunfeng was embarrassed by this.

``No, that’s, that’s not it, that’s, that’s, your daughter’s hands were very cold, so I was worried that there might be some discomfort?''

``It’s cold-''

"No, no, no. Ciyu was healthy. Being healthy was our Ciyu's only good point. Our Ciyu was healthy, which was good. Right? Ciyu? Our Ciyu was the best, right?"

"huh!"

Qing looked very refreshed.

I don't think I'll miss Yi-mei for a while.

No, um, but I still want to see Yi-mei, that feeling, that softness, I can't express it.

Qing glances at Sima-lang with regretful eyes, then quickly puts on his clothes.

At that moment, Sima Chunfeng's small eyes flashed!

Although she was shorter and therefore more feminine, her head was higher when she sits, giving her a dignified appearance. She was Sima Chunfeng, who has already achieved two victories against Heavenly Blossom Sword.

This time, in order to make up for the evenly matched scores, Sima Chunfeng, as the world's most talented woman, was trying to enter a fair competition.

Indeed, in terms of daggers, the Sima-lang was the best in the world, and since the Sima-lang has a low center of gravity and was stable, this time the Sima-lang takes the lead with two more victories… …

``Come to think of it, you went to the Wulin Alliance again? I felt bad the moment I got back.''

``Haha, this was it, Heavenly Blossom Sword. You’re changing the subject because it’s disadvantageous? You’re so cute.''

``Huh?''

"And this was a grave mission, one that should be undertaken by Sima Rang, a task that cannot be entrusted to the foolish soldiers of the Operation Party. The Cheonhwa Sword has done a good job, haha. This was worthy of being called Sima Rang's close friend."

As soon as Sima-lang returned, it was decided that he would join the Wulin Alliance again.

The Geomyeongpa and Geomyeongsan Mountains in Guiyang County, Guizhou Province were famous mountains representing the region, but it has been discovered that the old prestigious family that resided there was now a den of the Blood Cult's Shiksimdan.

The hometown of the three idiots, the villages of Bangmilgok, Jangmilgok, and Jomilgok, which were connected by blood ties, have also been located.

Moreover, there was information that the closest aide of the Sub-Sim Demon Army (the guy who claims to be one) was staying in Laosan County below.

This was obviously a serious matter that the Wulin Alliance must directly address.

By the way, I decided to leave the three idiots of the Blood Cult alone.

It was Sima Chunfeng's opinion.

I would like to bring you in as a warrior of the Wulin Alliance and put you in a low-ranking position. Is that okay?

Naturally, they'll come into contact with the Blood Cult, so they might be able to capture that secret line. They might also be able to spread false information to the Blood Cult, causing confusion.

Or, if you enjoy a comfortable life in the Zhongyuan, you may be accepted someday.

Qingdo, well, other than the fact that they ate cannibalistic elixirs, they weren't originally people with particularly high levels of evil karma.

Although he committed the heinous crime of daring to feed me elixir and providing nutritious food to the drunkard, I can still say that there was room for leniency.

Sima Chunfeng leaves again, and the days of the swordsman pass.

The Sword Master's Morning.

After the morning roll call, the assembled officials stand in a neat line in front of the stage and wait for the audience.

A voice that bursts out all at once when the blue light comes on.

``````Hello!!! Good morning!!!''''''

The Qing never gave him formal training.

At some point, they were all officials whose voices began to overlap as if they were one.

If our hearts were connected, then it can happen. Yes.

Look at it now.

These eyes sparkle with a passion for learning. It's a thirst for learning that I simply can't ignore.

Qing meets each of their eyes and responds with passion.

Of course, it was mid-July, and it was full-blown summer, so I wondered how the officials would know if their eyes met or not.

``The instructor saw me! He turned his head and looked me straight in the eye!''

``It would be Lady Chang, not you.''

"No, you chose me! You will lead me beyond the realm!"

You see, hearts were meant to connect.

It may seem strange to cover your face with a cotton blanket in the summer.

Qing was enjoying the cool summer better than anyone else, with the cool air of Hansimgong rising inside.

However, in fact, the school building was not very hot.

Mt. Yosan, originally a high western starting point, was the starting point where the temperature drops sharply, and it was a slope where seasonal winds blow harshly all year round.

There was a valley there, so even in midsummer, it was cool at night.

The reason the Department of State Affairs was built in this valley in the first place was because of the cool temperature. Why would they schedule the academic year in the middle of summer?

Rather, there was something hotter than the heat in the mountains.

It can be said that the passion of the officials, who were burning with love for swordsmanship, was much hotter.

``If it’s a buungchak shak shak, wouldn’t it be better to have bungeo or waek in my food?''

"No, I threw it as a check to prepare for the next "Kangjungganggang." Wouldn't that allow for a smooth transition from "Kangjungganggang" to "Buung?"

``But wasn’t it destroyed by my sudden attack just now? It was just a herbivore showdown, so I stopped here, but what if I get caught in a counterattack that goes like a slap before it goes from strong to strong like you said?''

``Hmm, that makes sense, but…''

Now, the three secrets of the Samro Sword were completely mixed and the practitioners were in training.

If others heard this, they would wonder what on earth it was, but surprisingly, the overall level of swordsmanship was growing like bamboo shoots after a rain.

The best study was the study you do on your own.

In fact, the swordsman was in an abnormally overheated state.

Aren't these people, buried in the mountains, eating three tasteless meals a day and having nothing else to do, devoting all their time to training?

You might say that I'm studying because I have nothing else to do.

None of the people who say that have ever studied because they were bored.

Rather, in such situations, people tend to become more spread out, lazy, and strive to become more lazy.

Even if you don't go far, if you have experience of serving in the military in the homeland of the Qing, the truth was clear just by looking at the reality of compulsory education before military service.

If class isn't fun, you can doze off, doodle, or secretly send text messages. You should never study, even if you have nothing else to do, were bored, and can't avoid it. Of course, this was a great cause to avoid being defeated by the blind and impersonal education system!

So, the academic atmosphere of the swordsmanship academy was clearly an abnormal, abnormal realm.

There may be several factors for this.

First of all, most of the officials were from Korea and the US.

Since they were people who were passionate about learning from the beginning, their motivation was high.

Needless to say, he was a former ronin.

For those who were local martial artists and have local reputations, training was a continuous series of running, crawling, and jumping all day long to build the basics, but when I entered the swordsmanship school, I was surprised to see that, except for the first few weeks, I skipped all that and learned by swinging the sword to my heart's content, so naturally, every day was new and exciting.

Thanks to this, this passionate atmosphere has become established as normal.

Humans were creatures who were very vulnerable to the atmosphere.

It's never easy to be lazy when everyone was working so hard together.

Moreover, how profound and amazing was the teaching of Instructor Ximen!

He personally led the Yang Qi Trainee to first-class status in the entrance exam, and there were already two other Trainees who had achieved first-class status.

If you ask Qing, he'd say that they were just officials who had accumulated experience through their long life as ronin, and it wouldn't be strange for them to become first-class at any time.

From the perspective of the officials, how could they not be surprised and impressed when someone who had been nagged at and beaten a few times suddenly rose to first-class status bowed deeply and shed tears?

In addition, there were those who suddenly become more skilled, including the three idiots, and even those who have become people themselves, such as the dog.

The experience of seeing guys I thought were on the same level as me suddenly become far ahead of me was even more terrifying than I thought.

So, the atmosphere was that we should all study together.

The pressure of falling behind if you play.

I even hope that if I work hard, the instructor will look after me.

The swordsman was literally on the run day after day, like a horseless carriage going down a slope, like a thirteen thousand pound cart with a broken brake.

The results were tangible.

Episode 1. The King of All Diseases.

Sword Mastery Championship Winner.

What was the Manbyungjiwangjeon?

The pride of a weapon-wielding warrior, an extra day out, but above all, a special meal, snacks, and drinks—it's a once-in-a-lifetime match where everything was at stake.

Of course, there was a little bit of a hit or miss.

"Hey, Qing-ah, how do you guys get such a good vibe? These guys were always looking at that damn Sani's face, so they don't know whether or not they're swinging their swords. Those guys just put on airs to impress that crazy woman."

Peng Cho-ryeo's expression had become increasingly fierce lately.

One of the three officials was a woman, and she was more interested in the ashes than the ancestral rites, so she came out wearing makeup and pretended to be weak and staggered.

Besides, I don't understand why he made up his face but tore up his official uniform and got it dirty, making him look like a beggar.

"And what, oh my, I'm so embarrassed I can't even watch. Why can't these bitches bare their breasts? And when they do that, the men get focused, don't they? Seriously, these days, what the heck was going on?"

"ah."

I feel a little sorry about that.

It's like that again… … .

"Really, Qing-ah, you're the only one I have. After your school schedule was over, don't you want to go home? Just, let's meet my parents and have a meal together. Yeah, I'll break your neck, what's a neck? Even if it means emptying out my family's storehouse. Then I'll be full, and for ten months…"

``Well, I can’t eat that much, and I can’t be in your care for ten months either…''

But, thanks to that, Choryeo also seems to have lost interest in such uncultured followers?

From the mountain's perspective, it's a win-win situation. After all, Choryeo won't have to bring in a strange woman.

"The martial arts school's disciples were quite enthusiastic, but they still can't compare to the swordsmanship school. I didn't know my Heavenly Blossom Sword would be so adept at teaching. We're within the same school walls, so I wish their passion would spread a little."

Even the instructor of the martial arts department, Yu Wook-ah, could not hide his envy of the academic atmosphere of the swordsmanship department.

So, Qing cautiously makes a suggestion.

"Well then, how about trying shock therapy? There's the Manbyungjiwangjeon this time. What if I win the Sword Master's tournament, lose the Grand Master's tournament, and get 50\% in the Martial Arts tournament?"

The swordsman was already full of motivation, so I think it will have a more positive effect after winning.

The Grandmaster uses the shocking defeat report card as an excuse to treat the players very harshly, making them cry and snot.

They say the atmosphere at the martial arts hall was good, so I think the martial artists will be able to feel a little more motivated because they won.

So, the match-fixing was done in good faith, and the match-fixing table was rigged for the officials.

This was the truth about the victory of the Manbyeongjiwangjeon Sword Master.