\chapter{One Lucky Day (4)}

Qing examined Plunder Demon's weapons.

First, she excluded long weapons like spears, staves, and halberds.

In a close combat, the advantage of distance brought by the length of the weapon, or in her homeland's term, range advantage, was undeniable.

If two fighters were equally skilled, the one with the longer weapon would win eight or nine times out of ten. In the Zhongyuan they called this 'Shi You Ba Jiu'\footnote{十有八九, lit. 'eight or nine of ten}, meaning the results was obvious.

Of course, when it came to the fight between martial artists, it wasn't that absolute.

Assuming both fighters had equal skill, experience, and eloquence, the one with the longer weapon only had a slight advantage.

Beacause martial artists had techniques to overcome the disadvantage of reach with their Qi.

But the gap between the Flower Realm and the Profound Realm was as wide as heaven and earth. And now a Profound Realm opponent had the advantage of reach with a long weapon?

\textit{What a dirty tricks, this won't do. Really.}

Qing's gaze shifted to the weapons at the Looting Demon's waist.

One sword and three sabers. A zhidao\footnote{直刀; straight saber}, a guitoudao\footnote{鬼頭刀; demon-head saber} and a nanyadao\footnote{南牙刀; southern teeth-saber}.

\textit{Rather than a sword, a half-sword should be easier to deal with.}

\textit{And at the Profound Realm, he could deliver crushing blows regardless the weight of the weapon, so it will be harder to counter the zhidao.}

\textit{Well then, if I had to choose between the guitodao and nanyadao, I'd rather face the guidou, a more conventional saber.}

Nanyado was a type of sword with a sharp saw-edged blade. It was a vicious weapon that could tear flesh with the slightest graze.

Even if he held back, a major disaster could occur if it turned into a life-or-death fight.

"Uhh, then the guitoudao."

"Good choice. It's also my personal favorite."

Qing's mind sharpened.

"When you say ‘personal favorite', does that mean you usually use a saber, specifically a guitoudao?"

"Indeed. Maybe it's because the martial art I mastered is saber-based, or because my temperament suits the guitoudao, it's the one that feels most natural in my hand."

\textit{Damn it, I chose wrong.}

\textit{Even though he gave me the choice, I ended up picking the one he specialized in. Trying to outthink him had backfired.}

"Uhh, this might sound petty, but can I change it? Wow, your sword looks nice! I'm a swordsman too, so how about a sword duel?"

"It's already too late. I don't know why, but everyone picks the guidou saber when given the choice."

Plunder Demon grinned savagely.

Qing realized she'd been played.

It wasn't that he carelessly carried the full armory.

They were all weapons that were harder to counter than the guitoudao, so most opponents would chose the guitoudao.

\textit{How could a Profound Realm master resorting to such a cheap trick…!}

Of course, if he's a fool, he wouldn't such profound heights.

Or perhaps he was so simple-minded that he approached martial arts in a completely different way.

Plunder Demon untied his weapons and tossed them aside.

Holding the guitou saber, he gestured at Qing.

"Come at me."

\textit{I just mixed things up for no reason and now I'm losing my killing intent…}

\textit{No, if I could kill him, I should.}

Qing, recalling Plunder Demon's Evil Karma, steeled herself.

\textit{This robber looks plain and easygoing.}

\textit{But his Evil Karma isn't the same.}

\textit{How many people had he killed just to steal their martial arts to accumulate such bright red 500 Evil Karma?}

\textit{Even if that wasn't the case, a Profound Realm master who hid his strength and secretly steals martial arts is a dishonest person.}

Qing raised Moonlight Sword high.

She inhaled sharply and squeezed her dantian fiercely.

The Qi pouring out of it violently sweeped through her meridians in an explosive flow.

Suddenly, the world tilted.

The world leaned toward Qing.

The world was pulled in by a person, such was the sword of the supreme being that stood both above and below heavens. 

\textit{Nine Swords of Solitude. First Movement: I Alone Am Supreme.}

Wherever the sword pointed, the heavens and the world must tilt accordingly.

As soon as the fight started, she used the ultimate move.

Well, why would anyone waste time if given the opportunity to do the first strike against a Profound Realm master?

Gong Ryang Sayun leaped back in shock.

In the worldview of Heavenly Martial Emperor, there were no others but only oneself, thus it was the manifestation of violent thoughts that distorted the world without a peer.

The world tilted, and with Human-Sword Union, the swordsman vanished behind the sword's presence, leaving only a single blade standing tall.

Plunder Demon's relaxed expression shattered, his lips twisted, and his jaw clenched, because he had to clench his teeth.

His guitou saber glowed crimson with enhanced qi.

A Profound Realm's Qi shone too brightly to be called just a starlight

Blood-red light spurting out in all directions.

Soon, the sword that tilted the world as if it will split it in two, the central axis of the universe and the guitou saber were rapidly approaching-

Clang!

The guitou saber was knocked back violently.

Plunder Demon's flew up as if he was souting 'Banzai!'.

His head tilted toward Moonlight Sword's sunset-colored Qi, as if offering itself to be split in two.

Then—

The guitou saber struck again.

Countless afterimages followed.

No, it was not afterimages.

All those afterimages were a real strike, and soon countless clashing sounds erupted, like a thousand bells being struck.

Qing gritted her teeth.

Dozens of impacts hit simulatneously, and the shock from the sword going through the handle and hitting the palm of the hand caused a tingling, almost tearing pain.

This was the extreme Philosophy of Early-Stage Profound Realm.

Towards the sword that stretched only upwards.

A sword that is swung repeatedly, tens of thousands of times, as if trying to break that one point.

As the ten thousand swings continued without end, there was a grand will there to never rest until it was done, until the enemy was cut down.

Qing marveled at his sheer determination.

Hundredfold Practice Saber Technique. First Movement.

Water Droplets Wear Away the Stone.

Hundredfold Practice Saber Technique was a basic training technique that was intended to lay the foundation of wielding a Dao rather than being practical.

As it was the first Movement of this technique, it was perhaps natural that it contained the Imagery that one should train without rest, and to continue to train endlessly, just as a falling drop of water wears away a rock.

What about Nine Swords of Solitude?

It was a perfected martial art that can be seen from the heavens above and the world below, by someone who has already reached the absolute realm.

So, its First Movement Imagery contained the declaration of Heavenly Martial Emperor.

'The perfect sword has already been completed.'

And now that perfect sword was struck by the sword of a human.

A hundred strikes, a thousand, perhaps ten thousand strikes.

Then—

Crack!

The world tilted by Qing's sword shattered in an instant.

As if it had always been that way, the earth was below and the sky was above. The only thing that had changed was Qing's figure was sent skidding back, both feet scraping the earth.

QWing swallowed the burning heat that rose in her throat.

It was because her all-out attack had drained her Inner Qi by a third, her meridians were in turmoil, and she suffered internal injuries.

The pungent, fragrant, and gritty smell of iron and saltiness clung to her mouth as if it filled her nasal passages.

But Qing's eyes burned with fighting spirit.

\textit{Profound Realm, this is Profound Realm.}

\textit{But it was worth a try.}

\textit{The idea of the same technique continuing infinitely is astonishing, but thanks to it, I am able to clearly understand what kind of martial arts it was.}

\textit{The martial art itself, at best, is blue.}

\textit{It's a crude, unpolished martial art without any technique. It's probably an introductory Orthodox martial art.}

\textit{However, borrowing the time units of my hometown, these basic strikes were performed at intervals of several hundred times per second.}

\textit{Still, the martial arts themselves are crude and simple.}

Qing stomped her right foot—

Heavenly Demon Reigning Step exploded forward, scattering remnants of demonic energy.

Then, Qing's sword traced countless afterimages—

One Hundred Eight Asura Sword, Eleven Thousand Strikes.

An endless series of strikes, swung recklessly with beastly ferocity.

The Looting Demon's afterimages multiplied in response.

The four most fundamental swordsmanship stances—downward slashes, horizontal slashes, diagonal slashes, and full-body swings—seemed to overlap in an infinite number of possible combinations.

The sound of swords clashing with sabers continued unceasingly.

As if thousands of blacksmiths were each swinging their hammers, the clash of blades and Qis scattered sparks.

Suddenly Qing's sword shifted.

The sharp sword that had been digging into the empty space to take advantage of any gaps suddenly became elegant, like countless waves that surged forward.

\textbf{Yue Maiden Sword Art. Eighth Movement: Moonlight Has No Regret.}

Three streams of qi surged forward like tides, but the maiden wielding the sword remained indifferent.

Qing saw her, the Yue Maiden.

A woman who lost her beloved in war.

In the world, she had been the only person, until a man made her a woman.

But now that she had lost his lover, there was no reason for the woman to exist either.

Fate was a vain thing.

Because she met him, her world was to be with him, and the reason her heart broke was because he was no longer in the world.

'If we hadn't met in the first place, you and I would have just existed in our own worlds.'

And so, Yue Maiden turned her back on the world.

If there was no meeting, there was no parting.

The sun chased the moon, but the moon ran away and did not meet it, so the sun existed as the sun and the moon existed as the moon, and day and night existed separately.

Who said the moonlight was lonely?

The moonlight just flowed, there was no regret.

Yue Maiden's choice was to become complete and alone again.

When she was alone, Yue Maiden was just a happy child with no name, no gender, and not even human.

Only after meeting the man did Yue Maiden realized that she was a woman and a human being.

Yue Maiden transformed to a woman and a human being.

'I' only existed after meeting 'you'.

On the contrary, before meeting him, she was nothing but nature itself, the entirety of the world.

So Yue Maiden returned to the mountains and becoming nothing but nature again.

And rejecting fate, she remained alone, never to change again.

\textit{Ugh, there really is no martial arts in the world that can be trusted.}

\textit{Nine Swords of Solitude tells you to just throw away everything and spend your life training until you die.}

\textit{Yue Maiden Sword Art if you never met anyone, you would be perfect and unchanging, immutable.}

\textit{Why are you all so negative?}

\textit{If you're going to give up everything and live alone, what's the point of training and becoming a master?}

\textit{Isn't saying you won't meet someone because you're sad about breaking up the same as saying you won't eat because you'll get hungry again?}

\textit{No, why did Yue Maiden made such crooked statement at the end?}

For a moment Qing's sword wavered.

Since the swordsman did not agree with the swordsmanship's Imagery, a certain disconnect naturally occurred.

How could a Profound Realm master missed such opening?

"Shit, wait, wait—!"

Until now, the Qing had been on the offensive and Plunder Demon had been counterattacking, but now their positions had been reversed in an instant, and Qing was busy blocking Plunder Demon's countless attacks.

Reversal of offense and defense!