\chapter{One Lucky Day (5)}

Profound Realm master's skills were nothing to be surprised about. If a Profound Realm master showed Profound Realm's strength, why would anyone be surprised?

However, the sight of Qing, who kept retreating but still managed to ward off the countless quitaodao trails, was truly a remarkable feat.

The expression 'Transcendental Harmony' that Qing jokingly called herself was truly worthy of recognition.

But Qing's expression gradually becomes more and more rotten.

Backed into a defensive position against Profound Realm?

What other reaction Qing could have shown? After what has she been doing so far?

After escaping with Subtle Wave-Treading Steps, she was busy running around like a rat with its tail on fire, running around aimlessly.

But somehow, Qing was able to fight back.

Why?

Well, that's because Plunder Demon was only observing.

Plunder Demon's goal was Qing's martial arts, so he had no intention of killing Qing.

He heard that the other leader of the cult were burning with resentment, shouting, "Graaah! I will kill Seomun-Qing at all costs! I will kill her no matter!"

Well, that's their business, not Plunder Demon's concern.

Rather than killing her?

If he caused serious injury or permanent damage, she might lashing out, saying, 'You did this to me and still expect me to give you martial arts skills? Just kill me, gut me!', so he couldn't help but be even more cautious.

Usually, the person who was regretful should be the first who fold, so wouldn't the person who was regretful now be Plunder Demon?

Qing was well aware of that fact.

So, the enemy can't use his weapons on me, but I can use them freely.

This calculation was also behind the extremely vile current Heavenly Killing Star's willing acceptance of Plunder Demon conditions.

But?

Qing's expression gradually became more and more rotten.

\textit{Why is this makes me angry?}

It was an unavoidable characteristic of martial artist.

Now that Qing had gotten her hands dirty in Wulin, she started to think like a martial artist.

While she was rushing at him with every intent to kill, the other person responded with nonchalant attitude as if they were doing some chores, as if telling her to keep going until she was exhausted, so of course she couldn't help but get angry.

Kkwarung!

Purple Lightning Demonic Qi, responding to its master's wrath, willingly rose and unleashed purple lightning.

When you heard the sound the lightning, it already strikes and too late to defend, so the purple lightning stroke Plunder Demon's shoulder.

Although it wasn't enough to break through Profound Realm's Protective Qi, it was enough to create a brief, fleeting opening.

Qing, who was taking a step back, suddenly puts her weight on her back leg and stomped her front leg in reverse.

At the same time, the Moonlight Sword drew a diagonal line.

The most perfect straight line connecting oneself and the enemy.

Emperor Sword Form

The emperor simply sat on a high place, pointed at the enemy, and annihilated them. The one who moved the world with his simple fingertips was the emperor.

In an instant, the figure of Plunder Demon split into two.

One remained in his position and was cut by the Moonlight Sword, while the other stepped back and stood with some distance between them.

It was a technique called Transposition\footnote{移形換位; 이형환위}, which was a phenomenon in which an afterimage was left behind by moving quickly in an instant.

Plunder Demon suddenly felt a chill.

The hem on the chest of his clothes was torn, and the cold air of early spring in Liaoning touched his skin.

But a smile appeared on Plunder Demon's lips.

Just now, it was a move that almost put even himself in danger.

Overwhelming majesty unfolds in a single thought!

A perfect move that combines attack and defense, cutting off the flow with a single stroke and dominating the situation!

\textit{The severing move must have been a very extraordinary Divine Art.}

Plunder Demon couldn't stand it anymore and shouted!

"Good!"

"Bullshit!"

A furious roar echoed in response.

But the sound was coming from up in the sky.

When Plunder Demon lifted his head, he saw Qing's figure crouching upside down in the air.

Soon, Qing shot down to the ground like a cannonball, with the force of a meteor falling.

Great Meteor Demonic Staff ultimate move, Meteor Fall.

Boom! There was a thunderous roar. The frozen ground shattered,sending up a thick cloud of dust.

And then, breaking through the dust, Plunder Demon with a great saber in front of him slide back with the same posture.

Then, Qing pursued him with a new attack.

With the upper body forward while floating in the air, the right hand holding the sword was pulled completely behind the left shoulder.

The Moonlight Sword was covered in a sunset glow, and a fiery red thunderbolt swirled around it, roaring. The moment she swung the sword and brought it down, a single red thunderbolt connecting the sky and the earth strike down violently.

Blood Shadow Thunder Lightning Dao Method, Blood Shadow Dragon Breaking Mountain.\footnote{There's a pun involving EEG and bankruptcy}

Plunder Demon held the back of his guitou with his left hand and raised it in a flash.

Immediately after the collision, a power struggle between the two began, with Qing, who was swinging her Moonlight Sword, frozen in mid-air.

However, the blade of the Moonlight Sword was slowly being pushed back.

At that moment, behind Qing's veil, three blue flames bloomed in her pupils and began to rotate.

At the same time, countless waves of Qi rippled along the blade of the Moonlight Sword, which then began to rotate violently.

One of Ten Great Demonic Arts Under Heaven, Chakra Wheel Demonic Tribulation!

In both density and power, there was a significant difference in the strength of the Harmony Realm and Profound Realm.

However, regardless, despite of Qing's realm, her Sword Force slowly began to penetrate the quitou saber and into the Plunder Demon's Sword Force.

The startled Plunder Demon reversed his stance.

Qing swung around and landed surprisingly gracefully, despite the fierce struggle just a moment ago.

Then, the image of a giant hand, infinitely white and pure, yet at the same time distorted and hideous, filled the field of vision.

"White Hand Demonic Art!"

After Plunder Demon shouted, it finally dawned on him that the strange energy just now was the Chakra Wheel Demonic Tribulation, so wasn't the purple lightning strike technique before that was the Purple Lightning Demonic Art?

Qing took advantage of the momentum and pushed even harder.

As the bell rang, the Tathagata Divine Palms unfolded, and at the same time, she leaped forward and extended her sword.

Sometimes, she would extend her sword-holding fist, unleashing a devastating strike that didn't exist. The strange swordsmanship, which glided past the enemy's blade with a flick of the wrist and passed through like a ghost, was the mysterious technique of the Life-Saving Saber.

All kinds of martial arts swirled around, each changing with a different Imagery.

When it surged, it was like a fierce wind, and when it mixed in with others, it was silent like a tranquil forest, and when it feels like killing intent was burning hot like a flame, it was also like a mountain, standing firm and unshaken.

Truly unpredictable, this must be what Furinkazan\footnote{風林火山; Wind Forest Fire Mountain; Takeda Shingen's battle standard, based on Sun Tzu's 'The Art of War'} looked like.

Meanwhile, Plunder Demon's subordinates were mesemerized watching this astonishing battle.

And a Living Jiangshi was also watching this fight with interest.

She wasn't just a spectating, as she was constantly moving their mouths, muttering and talking silently.

"Sister Yuhwa, Heavenly Blossom Sword and Sword Demon are currently fighting. If there's anyone curious about it, could you connect me with them? I'll relay it to them in real time."

-Really? Heavenly Blossom Sword?

-Wow, where are you? Changbai Mountains? Uwaah, it's too far.

-Is she that beautiful? Have you seen it in person?

-'Everyone, shut up,' the master said. 'Oh, this is going to be fun. So, what's going on? By the way, Yuhwa, are you imitating my voice right now? No, cancel that. Anyway.'

So, Gongryangsa Yoon began to relay the details of the confrontation between Qing and Plunder Demon to the sisters scattered throughout Zhongyuan.

Was this how Qing's skills leaked out without her even noticing?

"Oh, Heavenly Blossom Sword is swinging her sword fast, really fast. Sword Demon is also fast, so the sound is really loud. It's like, clang clang clang clang clang clang clang."

"Oh, Heavenly Blossom Sword is being pushed back."

"Oh, lightning just struck. That's amazing. Heavenly Blossom Sword is just flying around and swinging her sword, and, whoa, a huge palm just slammed into Sword Demon. Oh, and then her swordsmanship, wow, that's fast. Really fast. Like, shashashasha-fast."

-Sa-yoon? Is that the best you can do?

-Sister Gongryang, are you calling that narrating?

-Ugh! If this is what's going to happen, then why on earth did you say you'd tell me?! You're just bragging about meeting Heavenly Blossom Sword right now!

-The master says, 'Oh my, Sayoon, is that really the best you can do?'

"Oh, I'll do my best. Oh, so, Heavenly Blossom Sword jumped and swung her sword just now, three or four times? It's incredibly fast. Sword Demon kept blocking, but yes, he blocked well. This is a showdown that makes the ground shake and your heart race."

-No, who swings a sword that slow!

-Sister, are you doing this on purpose? How can a person's expressive skill be this miserable?

"That's a slander. I simply relayed the scene exactly as I saw it. Please don't blame me for your poor imagination."

-Oww! What the hell are you looking at! Unnie Gongryang, explain properly now! Explain properly!

-The master took a deep breath and went for a walk with her dog.

-Oh, Chugu. I miss Chugu. Is he really that ugly? Just how ugly can he be? I like ugly dogs too.

Fortunately, it seemed that Qing's skills did not leak out.

Plunder Demon's condition was not good.

His clothes were tattered, and his exposed skin was cut and blood was running down it.

Compared to that, Qing was relatively clean, just covered in dirt.

Anyone would think that Qing had won, but…

Shit, I lost.

Qing's face crumpled.

By conventional means, there is no way for Qing to defeat a Profound Realm master.

To be precise, if a Profound Realm enemy was extremely angry that their eyes rolled back, and they rushed in with a state of 'I will kill you even if it means suffering losses to myself', then she had a chance of winning.

Then, wouldn't it possibly for her to take their life just by sacrificing a few injuries?

But what if that enemy remained calm and unperturbed?

There was no way for Qing to fight back.

If Qing was in Late-Stage Harmony Realm, and could roughly see and determine the path to Profound Realm, then that's another story.

To the Harmony Realm Qing, that path was still a vague unknown, just a monster existing in the human world.

"Is thas it?"

"No, don't you even get angry on a human level? If a Profound Realm master get beaten up by a Harmony Realm, you should be furious at losing face, your eyes rolled back and shouting you'll kill me. Are you even human?"

"Why should I be angry with you? It's my own fault being a terrible Profound Realm master. There's no reason to blame you."

If it weren't for his Evil Karma, he would have had the appearance of a truly peerless master, but since it was the words of a martial arts thief who went around stealing other people's martial arts, it wasn't particularly convincing.

"Rather, thanks to you, I have gained confidence, so I am happy and have no reason to be angry."

"Are you sure?"

Then, the robber's eyes became blazing.

"Yes. I'm certain my thoughts were correct. Even though you entered Demonic Ascent and become a Demonic Adept, you possess the ability to subdue even the Late-Stage Harmony Realm. This is because you've mastered countless Demonic Arts. Isn't this proof that my gathering of martial arts to break through the realm was the right course of action?"

The eyes of the robber who spoke like that sparkled with a desperate madness.

However, it was a madness that felt somehow familiar, a look that seemed familiar, and Qing thought about it for a moment before-

\textit{Ah, he's on the same level as Sword Friend, a martial arts madman, a guy obsessed with martial arts. Of course, I can't win against a madman.}

Qing immediately understood the unusual endurance of the robber.

By the way?

"Demonic Adept? Me?"

"So, you're saying you're not a Demonic Adept? You seem poised to gather all Ten Great Demonic Arts Under Heaven. But I've already personally tested you and confirmed that your skill far surpasses even Harmony Realm, so I'd say you're a Great Demonic Adept among Demonic Adepts. Of course, I understand that it might be embarrassing for an Orthodoc martial artis to have mastered Demon Arts."

"Shit, is the 'Great Demonic Adept' really a real thing?"

\textit{It seems like there is a serious misunderstanding.}

\textit{But there's no need to correct it, right?}

And then the robber's eyes flashed.

"Now, it's your turn to keep your promise."

"Well, I don't remember making any promises. I do remember being threatened, though."

"Then, will you die?"

Qing shriveled at that.

"Do you know the Lunar Jade Maiden Divine Art? Just in case you don't know, I'll explain. It's a divine art that originated in a certain place in the North Sea. It. Is. Truly. Terrifying. In addition to its power, it has incredible beauty benefits—"

"What will I gain by learning the Inner Qi Method? Should I disperse my Qi cultivation and learn something new?"

"Oh."

I was planning to just teach whatever and send him away, but thinking about it, that's true.

It might be fine if it's high-level martial art of the same lineage that could be learned as is, but how many martial artists would learn another Method just because they obtained a better one?

Unless it's the ronin who are hungry for Divine Art, and Qing, who build up her Inner Qi through dishonest acts.

Qing checked the martial arts skills she had.

"Well, would you like to have the Wo\footnote{Japanese} Sword too? I got it after a thrilling, nail-biting match with that Japanese swordsman, Chusangryu\footnote{'abstract art'. another Ging's nonsense}, lasting perhaps seven or eight days."

"No work."

"What about the Vast Sea Sword? That vast ocean—"

"I know that too."

"Reflux Saber?"

"I already know."

"Reversing Stream Spear?"

"It's not a bad spear technique."

Even though Qing kept calling out the blue border martial arts, Plunder Demon knew that much as if it was a given.

\textit{Well, if he accumulated that much Evil Karma by robbing martial arts, wouldn't he had obtained at least the blue border martial arts?}

\textit{Looks like I'll have to come up with a red border martial art.}

"By any chance, Yanjiaguan\footnote{彦家拳; Yan Family Fist}-"

"Fist Art is a no-no."

"Isn't Yanjiaguan a famous martial art?"

"I know. It's a Divine Art, but if I wanted to learn it, I could have learned it a long time ago. But what's the point of learning Fist Art anyway?"

"Huh? You could have learned it? Well, since Yan Family was destroyed, it could have leaked. Then what about the Scattering Blood Claw?"

"I personally don't like Claw Method. What kind of man would use claw? Swinging iron claws on both hands is shameful and embarrassing."

"Aishh, you're being so picky. Hmm."

\textit{And then what's left is, um.}

\textit{Life-Saving Saber Technique, Great Meteor Demonic Staff, maybe?}

\textit{But Great Meteor Demonic Staff is a miraculous technique that allowed one to change direction in the air, it's too dangerous a martial art to hand over to a Demonic Adept.}

\textit{So, there is only one option left.}