\chapter{One Lucky Day (2)}

\textit{Swinging a sword on horseback certainly has a unique and unparalleled thrill.}

\textit{If I had to compare, it's less like slicing and more like tearing—raw and visceral. Hmm nice.}

"Eek s-spare me…! Gah!"

\textit{But why?}

Qing was lost in thought.

\textit{With the added momentum from the high vantage point and larger sr=wing arc, shouldn't it cut more smoothly?}

\textit{But why does it return with a violent jolt, with muscles and skin caught, bones broken and crumbled, and that ecstatic destruction?}

\textit{The violent sensation of the handle roughly hitting the palm, wrist, forearm, and elbow joint, wow, I can't describe it.}

"Split! You go that way!"

"Aaaah!"

"Waaah! Someone help!"

The Moonlight Sword, raised high, descended vertically onto the bandit's skull like an axe lodged in firewood.

Normally it would cleave through the spine and exit the back, but this time it stopped at the neckbone and stuck.

Suddenly a lightbulb goes off in Qing's head.

\textit{Ah. I see.}

"Why, why are you only chasing me…!"

The Moonlight Sword arced upward in a diagonal trajectory.

The arc created by Sword Qi formed a long ribbon, like trail stretching. like unfurled silk before meeting the bandit.

The blade dug in silently and smoothly.

Even after the sword passed through, the bandit took two more steps before his upper body slide off and plopped to the ground.

\textit{Hmm. That makes sense.}

Whether it's a sword or a saber, the essence lies in the act of slicing.

Let's think about the ingredient that a great man should cut when he drew his sword: radish..

To slice a radish, there must be motion, either outward or inward.

What if you held a knife and just press down on the back of the knife?

Rather than cutting, it was more crushing or chopping.

Swordplay and saber techniques are ultimately about slicing efficiently.

Thus they're refined arts, designed to maximize lethality through footwork and technique.

But on horseback, the high vantage point and simplified movements, turned every swing into an axe-like strike.

Naturally, the sensation was rougher.

\textit{Perhaps, horseback martial arts were techniques optimized for this very motion.}

"Gah gack…!"

\textit{Did the creators of these martial arts meticulously account for such details?}

\textit{Modifying martial arts isn't easy…}

Lost in thought Qing tugged the reins.

The clever Lu Bu understood and slowed to match the fleeing bandit's pace.

About half a \textit{shichen} later.

"Huff huff…! I—I can't…huff, anymore… Just,huff, kill me! Kill me!"

The man running ahead of Lu Bu finally collapsed, gasping for air.

Sprinting for half a \textit{shichen} was commendable, but he's clearly hit his limit.

"Kill you? Fine. Request accepted."

"Huff… N-no, wait, spare me…!"

"You want to live? That's also accepted."

"Huh? You'll spare me?"

"I'll count to five. If you get caught, you die. If you escape, you live. Ready? One, two—"

"Damn it!"

The man scrambled up and ran again.

But his pace wasn't the same.

Because if you wanted to run for a long time, you have to kept running even if you have to slow down. If you took a short break to relax your muscles, your body would already be loosened out and you won't be able to exert strength.

But still, the man ran.

His desperate sprint looked like someone's threatening him with a blade.

Well, Qing was literally threatening him with a blade.

And eventually—

"Gah! Aaagh…!"

The man suddenly collapsed, clutching his calf and writhing in agony.

He might have suffered a muscle cramp, or even a torn tendon from running too hard, far beyond his physical capacity.

"Tsk. You really don't want to live, do you? Should I count to five again? One, two, three…"

"Aaaah!"

But numbers meant nothing now. The bandit seemed to be unable to hear anything because of the pain, his heart pounding as if it was going to burst, his lungs squeezing, and the excruciating pain his whole body was sending out as it demanded breath.

"…Four. Five."

\textit{Well, I guess there's nothing I can do. I promised to kill you if I caught you. Ah, I really can't help it. I have no choice but to go through the trouble of disposing of a useless beast for the world. That's the promise.}

\textit{This man among men, Ximen Qing, must keep her words.}

A moment later.

Qing stretched,

Behind her mask, her smile was brighter than ever.

"Ahh, how refreshing. What the heck, a bunch of robbers have been swarming me since mid-morning. Is today my lucky day? Feels like it."

This was the joy of solo travel.

If you hang out with friends, you ended up in a group, so the bad guys couldn't attack you.

When luck was on your side, everything goes right.

Qing's good fortune didn't end with the morning bandits.

She got lucky again.

After a satisfying morning she felt peckish.

While chewing on jerky, an inn materialized out of nowhere by the roadside.

Of course, it wasn't strange.

Inns were often located on the roads where people traveled, and in this primitive society that had not yet conquered darkness, it was better to sleep comfortably under a roof, even if it was expensive compared to the condition of the room, than to sleep in the dangerous night.

But appearing just when she was hungry? A delightful coincidence.

Of course such inns by its nature tended to be pricey, but Qing's wallet was comfortably heavy.

"Waiter! Bring your best dishes quick. Three plates."

"Right away!"

It even tasted good!

\textit{The pork is made with dried meat, so it is a bit tough, but the spicy marinade made up for it, so I couldn't help but ordered more rice.}

\textit{The unnamed fish stew isn't entirely free of fishy odors, but the fiery spices masked it well.}

\textit{The spicy dumplings are a delicacy even Sichuan couldn't match, and the noodles are spicy and reminded me of back home. The soup had that throat-scratching kick, rare in the Zhongyuan.}

\textit{The stir-fried greens and eggs are bit bland and wilted, but it's addictively spicy, I couldn't stop eating it.}

\textit{Sure, the spicy flavors are a bit overpowering.}

\textit{When ingredients are subpar, or the cook's skills are lacking, nothing hides flaws better than spice.}

\textit{Since it is a remote inn where the freshness of the ingredients could not be maintained due to its location, the innkeeper's ingenuity to overcome this is truly outstanding…}

\textit{…This is bullshit!}

\textit{How much poison did these bastards dump in here?}

\textit{It tasted good though.}

\textit{A paralytic? Or a sedative?}

Sure enough, the kitchen staff kept sneaking glances her way.

Qing slammed her head onto the table to live up the expectations.

"Heh, the poison finally kicking in? Thought she'd never drop. Since the horse is so extraordinary, I thought she's a master who could brush off the poison and there might be some repercussions."

"Worried huh? Sell the horse and skip town then. But, damn she's tough. We emptied our poison stash and she still ate it all…"

"Must be a martial arts master."

"Master or not, that much arsenic would kill even the world's best. Let's bury her and scram."

"First, let's see her face. Just to be sure."

Well, of course.

Why else waiters were included among the five lowest professions in Zhongyuan?

It was a profession that could easily lead to a career as a human trafficker, robber, or rapist, so who would know what might happen in such a remote inn?

With her head on the table, Qing's limp arm suddenly shot out and grabbed the waiter by his collar.

"Gack."

"Wow, today's really my day huh?"

Qing's lips curled into a grin.

\textit{I had a refreshing morning and enjoyed a delicious lunch that I hadn't even expected.}

\textit{As soon as I finish eating, I get another workout like this, unbelievable.}

Her luck didn't stop there.

After dismantling the inn's staff-turned-bandits to small pieces and made a display, she resumed her journey

An arrow thuds into the ground ahead and blocked her path.

A classic bandit ambush.

\textit{Wow, like three meals in a day!}

\textit{Breakfast, slaughter, lunch, slaughter, dinner, and now another slaughter!}

But wait there's more.

At dusk she arrived at Fushun County and ordered a feast at an inn.

"You the owner of that black horse?"

"And you are?"

"I am Yi Taeryeong."

Here's a life lesson of Wulin:

When someone proudly announced their name in public, count to three.

One, two—

"Yi Taeryeong!" "The Twin Killers of Bai Mountain!" "Oh no!"

The Twin Killers of Bai Mountain.

By the sacred laws of martial aliases, if we roughly analyzed it, it would be like this.

Bai Mountain was Bai Mountain. 

Twin means a pair.

Killers were killers.

Clearly a nickname for a prospective Demonic Adept.

And if his alias includes 'killer', it was a proof that he was the kind of scum who deserves death without question.

"It is said that when the weak possesses treasures, disaster follows. This senior is here to help you."

Qing's grin widened.

\textit{What? Is it my birthday or something?}

\textit{Why's today so wild? A lucky day? And no one's even brought me soup\footnote{The plot device of Lucky Day. By this point Qing should've known she was raising death flag}.}

A short while later.

The infamous Twin Killers of Baek Mountain ceased to exist.

Thanks to the warm-up, dinner was delicious—went down smooth.

Just when she the thought the special day would end—

While buying snacks, a sneaky hand reached for her wallet.

Qing grabbed the wrist, grabbed his head to examine the face, and ran her eyes briefly over the head.

The reason for checking the face was that in the case of pickpockets, most of them were minors, so children get a pass.

And wouldn't there be a number on the head that only Qing can see?

But this one's old enough.

A life of sin, a beast in human skin, qualified.

Crack. The sound of breaking bone.

"Aaaah!"

Crunch. The sound of grinding bone.

"Grrk…!"

The pickpocket collapsed, foaming at the mouth.

\textit{It seems like he couldn't endure the bone-crushing pain while still alive. How could he be this weak?}

Leaving behind the fallen pickpocket, Qing hummed cheerfully as she strolled through the market.

\textit{Wow, what the heck is going on today? It's been fun all day.}

\textit{Is this my reward for living a good life?}

\textit{Seriously, I wish every day is like today.}

\textit{Come to think of it, Lu Bu's a real lucky charm.}

\textit{Aside from the pickpocket, weren't all today's villains—no beasts—were thanks to him?}

Qing's steps were as light as air.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Fushun County, Liaobin Inn.

The Liaobin Pagoda Murong Juhui mentioned was Fushun's landmark.

And in Zhongyuan, naming your establishment after a landmark requires prestige.

Thus the Liaobin Inn's name alone declared its status as Fushun's finest.

And Qing, a filthy-rich capitalist, always books the best room at the best inn.

Naturally she stayed at the Liaobin Inn.

And so did someone else.

"Sword Demon? I've always prided myself on having no equal in the world in terms of how much I eat. The world is vast indeed."

"Is she famished? How could she even all that in? Unbelievable."

Plunder Demon couldn't take his eyes off Qing's meal.

In this primitive era, the concept of mukbang was too early and too intense for the ever-bored Zhongyuan folks.