\chapter{One Lucky Day (6)}

Life-Saving Saber Technique (脫命刀法).

As the name suggests, it was a martial art that had a strong influence of Orthodox Taoism, as it was a method to escape from fate and overcome it.

At the same time, it was also the martial arts of Tuomingdao Odaesan, who was ranked 6th among the top ten martial arts masters certified by the Murim Alliance.

For reference, Odaesan's title, Tuomingdao (奪命刀), was written in a different Chinese character from his martial arts, meaning 'Life-Taking Saber', or a murderer.

It was quite insulting nickname for a top-tier master.

Because when you become a true master, you have the power to change nicknames you don't like with the edge of your sword.

But there was no particular fuss, and he himself was said liked that Life-Taking Saber title.

As expected from an Unorthodox leader, it seems that he thought that kind of vicious nickname was cool.

It was also a martial art that Qing acquired as spoils of war after beating the young master whose father was a Profound Realm.

\textit{But, that was okay back then.}

\textit{Because it was anonymous back then.}

\textit{In the end, it was ruined because of Yuanying, but somehow I was able to blame it on the Blood Cult.}

\textit{But it's different now.}

\textit{If I keep Life-Saving Saber Technique to myself and keep my mouth shut, it'd be fine, but if I share it others, problems would arise.}

\textit{But still, if I were to pass on martial arts, it would be better to pass on Life-Saving Saber Technique.}

\textit{Since it's originally the martial arts of Unorthodox's Great Demonic Adept, if it were to be passed on to another Great Demonic Adept, a martial arts robber, it would make sense, right?}

\textit{But I couldn't just let it go like this.}

Let's say that later on a problem arises, a master like Life-Taking Saber goes wild because his martial arts skills have been leaked and looks for Plunder Demon.

\textit{When Life-Taking Saber found Plunder Demon and asks about the source of Life-Saving Saber Technique, wouldn't it be a bit awkward if he says, 'Oh, that? Heavenly Blossom Sword taught me that? But your martial arts is good.'}

\textit{Master told me to pretend not to know and just ignore it if such problems arise.}

Actually, that'd be okay.

Qing spared no expense in unleashing all manner of Demonic Arts on Plunder Demon, including those from Ten Great Demonic Art Under Heaver, because she could have just pretended not to know.

Even if a notorious martial arts robber were to claim that Heavenly Blossom Sword of Orthodox faction collected Demonic Art, who would believe him?

The Unorthodox guys might believe it, but what does it matter whether they believe it or not?

Her Orthodox faction members won't believe it.

Still, the Unorthodox would believe it.

\textit{So, um, I guess should change the name of the Life-Saving Saber.}

\textit{However, the name of a martial art can be said to be the image and core idea that forms its foundation.}

\textit{So, if I were to change it, I should change it to something that has the same image as the word 'Life-Saving' and can be interpreted as such.}

\textit{If I just taught some random master, they wouldn't know, but if they're a Profound Realm master, they'll easily notice the discrepancy between the martial arts name and its core idea.}

At that, Qing's mind suddenly sanpped to a halt.

\textit{Let's see, the 'Life-Saving' part meaning to break away from one's predetermined fate, the fate of a mortal being, and achieve one's true self.}

\textit{Well, breaking free from fate, one's true self, destiny, the life ordained by heaven, the shackles, the oppression, if one wishes to break free from them all…}

While Qing was pondering, Plunder Demon waited quietly with a rather satisfied expression.

The martial arts she recited so far were rather common, so much so that even a local martial arts official could find variations on them.

But if she kept her mouth shut and thought about it for far too long, it meant that it was a martial art that was too valuable to pass up.

So, Plunder Demon was waiting with great anticipation for Qing's mouth to open.

But Qing's intention was merely a sleight of hand, to simply change the name of the martial arts, its Sutra and its Movement's names.

After a while, Qing suddenly extended her hand.

"Can I borrow your saber? A liuyedao\footnote{柳葉刀, willow-leaf saber} would suit it best, but still, any saber would be better to use than a sword."

"Oh, wait a minute. You guys, does anyone have a liuyedao? Give her one!"

At that, a man with his face covered by a black mask jumped out from the mountainside behind them, knelt on one knee, and offered his weapon respectfully with both hands.

Qing's eyes narrowed at him.

\textit{Cover your face? Only the most shady bastards who have to hide their faces from others go around with their faces covered. Look at that Evil Karma, what an absolute assholes. That's how it goes with a guy who covers his face. If they were honest, why would they hide it? They would have walked around proudly with their faces exposed.}

Qing (a veil lover, a master of making face-skin mask, always hiding her face) cursed inwardly.

But Qing was strong to weak and weak to strong, so she only cursed him inwardly.

There's nothing she could do in front of a Profound Realm master.

Qing slowly unfolded Life-Saving Saber Technique.

Because it was a martial art based on the principle of overpowering an opponent with force, the entire arm, from the shoulder to the fist, drew a powerful line.

Even in the midst of all this, wrist control was the key. The movement of instantly folding the wrist to bring the blade close to the arm and then raising it again, creating a slashing motion, was the essence of Life-Saving Saber Technique.

From the opponent's perspective, even if they've raised their weapon to block, it'd feel as if the enemy's blade suddenly passing through their weapon.

In front of Qing, who had shown off the first Movement, Plunder Demon had a very satisfied smile on his face.

"Indeed, it possessed an incredible depth. It's undoubtedly a renowned Divine Art. What's its name?"

\textit{Hmm, so you don't know Life-Saving Saber Technique.}

\textit{Before telling him the changed name, I demonstrated it just in case he knew about it.}

Qing responded with confident smile.

"It's called the Juche\footnote{North Korea's state ideology, part of Kimilsungism-Kimjongilism} Independence Saber Method."

"Juche Independence Law\footnote{A pun. 도법 can mean 刀法(saber method) but also 道法(logic and law)}!"

"Huh? Do you know the Juche Independence Saber Method?"

"No, I've never heard of it. But after hearing it, my heart feels somehow swell. I feel like I should applaud.\footnote{typical of North Korean government, military, and civilians whenever the Supreme Great Leader gave a speech}"

"…Right. This is the Sutra introduction, \textit{Juche refers to the great spirit of challenge that humans have, not conforming to nature and the environment, and independence is the instinct of life to break free from subjugation. Many people accept that human fate is in the hands of Heaven, that birth, aging, illness, and death are simply determined by Heaven, but that attitude is no different from that of a slave. So, to escape this fate, I convey the meaning of Juche and independence}."

"Hmm. Sounds good."

\textit{What's so good about it? Is Juche good?}

\textit{Isn't he exactly the type of talent they'd want in the North?}

Anyway, Qing taught him the Juche Independence Saber Technique.

She didn't want to fight a life-or-death battle with the Profound Realm master over a pointless trick, so she just changed the name a bit, but the essence of the method was still Life-Saving Saber Technique.

The robber's expression was now filled with a warm smile.

With an expression that seemed to embody satisfaction itself.

"Oh, then. Can I go now?"

"Hmm? Where are you going?"

"Hu, where? Now that I've taught you martial arts, we should both go our separate ways."

The robber shook his head at that.

"Haven't you had enough rest? Then you'll have to attack again. When will you have another chance to go all-out on a Profound Realm master without risking your lives?"

That was right.

Even though Qing had been beaten hard in countless sparring matches with her Master, she still couldn't unleash a killing blow.

Wouldn't it be a great opportunity to freely attack a more skilled opponent, without risking anything, something she couldn't while sparring?

Just hearing it makes it seem like Plunder was giving Qing a special treatment, didn't he?

Qing's eyes narrowed.

"And if I lose, I'll have show you my martial arts skills again?"

"Of course."

"No, what's this person's state of conscience? I'm not some kind of martial arts sack. Are you going to strip me of everything, down to my very foundation?"

Then, the robber's smile becomes filled with murderous intent.

"If you don't want to die, then you should do that, right?"

\textit{Oh, right. This son of a bitch is a martial arts robber.}

\textit{Now that I think about it, I'm really annoyed.}

\textit{The problem is that I fought using all kinds of martial arts just to find a killing angle.}

\textit{And now he knew that I have more than one or two martial art, so isn't it like showing off a thick wallet to a robber?}

\textit{Would a robber just walk away satisfied with I give a few bills?}

However, Qing was no ordinary victim.

Qing collapsed on the spot.

"Shit. I don't know. Then why don't I just die? Belly-cut."

"Hmm?"

"I'll just pack up all my martial arts and go to the afterlife. If I offer some Divine Arts to the grim reaper, I might just sneak off somewhere nice. Oh, it feels good to lie down. The ground feels so good."

Plunder Demon couldn't hide his bewildered expression at the sight of Qing lying down.

"Do you think I'm just talk?"

"It's the same whether I die this way or that way. I'm going to die anyway, so is there any need to give my enemy martial arts skills?"

"You're going to die anyway? I told you I'd spare your life if you just surrendered your martial arts skills."

"You know what? There's a story from Joseon. An old lady was going to the market to sell rice cakes when a tiger suddenly appeared and threatened her, saying, ‘Oh, I won't eat you if you give me a rice cake!'"

The expression on Plunder Demon's face remained absurd as the tiger story suddenly pop out.

"So, the grandmother threw a rice cake. The tiger bit the rice cake, got excited, and disappeared? The grandmother, shaking off her shock, headed back to the market, but after taking three steps, the same tiger blocked her path again. 'Ugh! If you give me a rice cake, I won't eat you.'"

The tiger, who said it wouldn't eat her, chased after the rice cake grandmother until all the rice cakes were gone.

Finally, when Grandma's rice cakes were all gone, the tiger laughed loudly and ate Grandma.

Because she didn't give it any rice cakes.

"Hmm."

"What's the difference? You'll keep fighting until I have no more martial arts to offer, then you'll kill me. In that case, I'll just throw away the rice cake and be eaten right away. I even wasted time teaching you the Juche Saber Method."

"Ahem, it's not like I intended to kill you, so I was thinking of backing down if you said you had nothing more to offer."

"How can I believe that? You said you'd let me go if I taught you martial arts, and then you immediately changed your words."

"Ahem."

Qing's ability to tread the line was close to the best in the world, even before entering Wulin.

Qing's sense whispered.

개겨도 된다!\footnote{expression of rebelling order and be an asshole about it}

It isn't her that have bad luck. Even Plunder Demon wouldn't be able to kill the treasured Plague Ghost with its bundle of martial arts, the golden goose that lays the golden eggs, Qing.

Of course, she had an intuition that he was not the kind of person who would easily give up.

Qing sat up and began to gently apply elasticity to that sly tongue.

"Excuse me, isn't trust especially important in situations like this? So what if I teach you a few martial arts and then tell you I run out of it? Would you just believe me and leave, thinking I really doesn;t know more?"

Gongryang Sa-yoon, who was listening, suddenly thought.

\textit{What on earth is going on, and what trust is needed between the robber and the victim?}

"Hmm."

"So, we can't betray the trust we've built, even if only briefly, with such shallow tricks and quick betrayals. I trusted Plunder Demon and taught you martial arts, and Plunder Demon trusted me and accepted that as the right decision."

"Hmm. That's true."

"And if you're going to keep tearing it down, you should at least give me time to catch my breath. What would I think if you asked me to give you more as soon as I gave you some?"

"That's true too."

Plunder Demon seemed to think about it for a moment.

"Then, I'll come back tomorrow."

"Aisshh. Are you kidding me? Martial arts aren't like coins you pick up on the street, and it's hard to even find one a day in this world. Let's meet next year. Let's meet right away next spring. Okay? That's fine. Let's meet when the flowers bloom."

"A year is ridiculous. And if you're already hiding among those sect masters by then, how will I find you? I'll come back in five days. What do you think?"

"Is learning martial arts easy? Then give me six months. Since we met in the spring, how about we meet in the fall?"

"Ten days."

"You're being so firm in your negotiations, aissh. I'm just cutting it in half."

"I also doubled it."

"That's not what I meant. It's not a matter of multiples, I just reduced the number of days. A year to six months is over 180 days—"

"Half-month."

"Sssss."

Qing pretended to stop.

The robber's expression was proud.

But in the end, wasn't the situation where they keep tearing it down for day after day already turned into a robbery once every two weeks?

In fact, since Plunder Demon had simply threatened with a knife, Qing had no choice but to make concessions, regardless of the robber's satisfaction, so it was a situation where one-sided concessions were being made.

This was one of the subtleties of trading.

When making a request, start with an outrageous amount and then reduce it sharply.

Then, the other party would quickly fall into the illusion that they were a great negotiator.

"Hmm, well, let's meet up once a season. Summer would be fine."

"…Twenty days."

"Then, let's do it for a month. Let's do it for a month! Exactly one month. It's early Second Month now, so we'll see each other in early Third Month! How about it! I'll just die if it's less than that. Seriously, I can't do it!"

"Haa."

The robber sighed deeply and stood with his hands spread open awkwardly.

Then, a black-clothed thug hurriedly put the weapons he had taken off from Plunder Demon's back, hung them on his waist, and put them back on.

In other words, they would not fight anymore.

Martial arts thief vs. martial arts robber, a sudden agreement!

Martial arts robbery once a month!

No one will understand what kind of agreement this is, but anyway.