\chapter{One Lucky Day (1)}

Lu Bu proudly raised his head as Qing looked down at the two who had come to see her off.

Murong Jun wore an expression of lingering reluctance.

Murong Chengyi had left at the crack of dawn without even giving Qing a chance to say goodbye.

At a time like this, the only son of the family couldn't possibly leave the Murong Family unattended.

"I wanted to go with Beggar Sister, but Father left too…"

\textit{Um, who said I'd take you along?}

\textit{Even Elder Sun-Moon Union wouldn't have allowed him to run off to such a chaotic frontier.}

\textit{Not because it is dangerous, but because there'd be too many scenes unsuitable for a child's eyes.}

\textit{But, well, thinking that way might ease the disappointment. Perhaps Elder had left at dawn precisely to avoid Junie's whining.}

"Young Lady Ximen, you'll stop by on your way back, right? I wanted to accompany you but with Jun'er here…"

Unlike Murong Jun, Murong Zhuji genuinely had to stay behind due to the Family Head's absence.

If any major decisions needed to be made for the clan, someone had to step in on the behalf of the young Moyong Jun.

"Ah! If you stay just one more day, we can visit Shenyang Tower, the best restaurant in Shenyang and go sightseeing together. Uh, Yaobin Pagoda, and then, umm ,also…"

Moyong Juhui trailed off.

Shenyang was notorious as one of the most unremarkable cities in the Zhongyuan, holding a status roughly equivalent to Daejeon's city Sungsimdang in Qing's homeland.

"Tsk tsk tsk, a friendship for a day is unforgettable for a lifetime\footnote{一日之交终生不忘}. We ate together yesterday, right? Even bathed and slept together. We did it all."

"Lifelong…"

"Huh? Don't you know? It's from the Book of the Later Han. True friendship isn't about how long you've known each other, but how deeply your hearts connect. Study harder, Young Lady Murong."

"Y-Yes…"

Murong Zhuji lowered her head in embarrassment.

\textit{Well, strangely, whenever I see Young Lady Murong, I feel like harassing her. Is it because she's always shaking?}

"Hey, just kidding, just kidding. Well then, Young Lady Murong, see you later."

"Yes! See you later!"

With that farewell, Qing clattered away on horseback leaving the Murong Family's estate behind.

Toward the Changbai Mountains and the Heaven Lake.

\textit{Might as well take a look while I'm here.}

\textit{According to Elder Riyue Xiangzhi, the chaos is concentrated around the middle and lower reaches of the Yalu River, near its source at Mount Changbai and beyond.}

It seems that such things did not happen in the vicinity of Dandong County, which is located completely downstream of the Yalu River, because the military was stationed there and security was maintained.

So first, she'd head west to Huanren County, near the border with Jilin Province, the Manchu's homeland, then make her way up to Mount Changbai, or Chanbai Mountains, while gathering information along the way.

The clip-clop of Lu Bu's hooves was unusually lively today.

Because he'd gotten new horseshoes.

Horses too walk more comfortably with fresh shoes, so he'd been in high spirits lately.

Though he seemed eager to run, he didn't make a fuss, understanding that galloping wasn't allowed within the city.

In that sense he was quite the clever fellow.

As they crossed Shenyang, envious gazes pierced through the air like arrows.

The more stares they drew, the prouder Lu Bu's long neck stretched, his head held so high, it was hard to tell whether he was looking ahead or at the sky.

\textit{Ah, so this is what it felt like to be envied.}

\textit{Back in my homeland, even the mid-sized domestic car my uncle had handed down couldn't compare to this level of prestige.}

The Moyong Clan's caretakers had been beside themselves over Lu Bu.

Despite their pride as a horse-breeding clan and the Moyong Clan's wealth, they'd never taken care a horse as magnificent as Lu Bu.

They'd praised him as a legendary Qianlima\footnote{千里馬; Thousand-Li Horse}, comparable to the famed Chitu\footnote{赤兔; Red Hare} or Wuzhui\footnote{烏騅; Dark Piebald. The general Xiang Yu's horse} their compliments brimming with genuine admiration.

\textit{With this level of prestige he might as well be a flashy imported car back home.}

\textit{Wait a minute, this bastard.}

\textit{Is he walking slowly not because we're in the city, but because he is basking in the attention?}

Regardless, the people of Shenyang couldn't help but marvel at the rare sight of such a magnificent steed.

The only downside was that while the horse was extraordinary, its rider fell short. Qing's upper body swayed uncontrollably with each step, struggling to maintain balance.

But thanks to that, the sheer mass created an undeniable ripple effect like the undulating waves of a massive tide.

"Hey, Husband? Your eyes are rolling back."

"No, isn't that one hell of a horse? Gah!"

"Hmph! I don't care. I'm going home."

But the men couldn't help feeling aggrieved.

Being drawn to such jiggling wave was almost instinctual for men, an irresistible cruel force.

Amid the growing number of pinched and resentful men, Qing and Lu Bu proudly traversed Shenyang.

Passing through the western gate of Shenyang.

Like any major city, the urban sprawl extended beyond the walls for a while.

But soon enough.

The tightly packed shops lining the streets gradually thinned, giving way to more residential areas.

Eventually scattered houses, fields, and empty lots appeared until at last the bare hills of the Changbai Mountains' foothills came into view, stripped by merciless logging.

Huff! Lu Bu snorted roughly.

Now that they'd left Shenyang and the roads were empty, he was eager to run.

"Tsk. Nope."

Qing tugged the reins, and Lu Bu annoyed clip-clopped forward with exaggerated steps.

Each jolting step sent Qing bouncing a foot into the air subjecting her to a horrific riding experience.

\textit{Hah, what a temper.}

But discomfort was the price of prestige.

And Qing's body was built like steel, unfazed by such jolts, while her ample rear cushioned the impact on her pelvis.

So even with terrible riding conditions, Qing hummed a tune.

Truth be told, she was in a great mood.

Why?

Because the day had started with a satisfying warm-up.

West of Shenyang, between the bare ridges of the Changbai Mountains towards Fushun County.

As they entered a valley with a clear path and rounded a bend—

"Halt!"

A carriage blocked the road, flanked by a few men with swords.

Behind her veil, Qing's smile widened.

"Why are you blocking the road?"

Her voice, though measured, betrayed a hint of giggle.

To the listeners, it might have sounded like nervous trembling.

"No need to be so scared. It's not like we're going to eat you."

The men puffed out their chests and chuckled.

Given that she was a woman with a sword, and considering the notorious deadly dangers of Wulin, they'd been somewhat tense.

But if her voice was shaking, well…

"Our elders can't pull the carriage because the horses are exhausted. We need some help. Your horse looks strong."

"And?"

"It'l be enough to just get to Fushun County. Why don’t you let your horse pull the carriage and you can ride in the carriage instead?"

"Is that all?"

"Of course not. The road's boring and there's nothing to do. With men and women together, there's plenty of fun to be had, right?"

The men burst into lewd laughter.

Behind her mask, Qing's smile deepened.

Back at Shenyang's gates, some guys had whispered and scurried off.

The ones following her were surely part of the same group.

That's why she'd endured the uncomfortable ride, so she wouldn't miss them.

And now a horseman came into position behind her, blocking the rear.

Three men climbed out of the carriage.

With vicious grins, they brandished their swords, as if telling her to surrender since they were bandits.

"Haah…"

Qing sighed in relief.

\textit{I would have been so disappointed if those who followed behind were innocent people.}

She stroked Lu Bu's mane.

\textit{Because I ride good horse, bandits just flock to me.}

\textit{Is this why everyone famous rode famous horses?}

Slowly she drew Moonlight Sword.

Sshhk— The finely forged blade hummed lightly, and as if sensing incoming battle, Lu Bu pranced eagerly.

But the men remained unfazed.

"Tsk. You'd really refuse fine wine for cheap liquor? If you come quietly, we'll spare your—"

"Enough. Go!"

Qing yanked the reins, Lu Bu, who had his front legs high, spun midair to face the rear.

Then the excited warhorse charged forward picking up speed.

They approached the horsemen fast.

Horses were naturally skittish creatures.

Unless specially trained, even minor disturbances could spook them. The sight of a charging warhorse sent the bandits' mounts into a panic, bolting forward uncontrollably.

Moonlight Sword was long enough to be wielded from horseback.

As the horses passed each other, a head flew into the air.

Splat! Blood sprayed high, and the bandit's horse, now even more startled, bolted toward the carriage.

Clatter-clatter! The empty carriage bounced noisily behind it.

Still unaware of the situation, the remaining horseman charged furiously.

Qing leaned forward, letting the sword's tip drag before twisting her wrist and swinging upward.

"Huh?"

A stupid last word.

The bandit's torso split diagonally, spilling its contents as steam rose into the cold air.

Then Qing leaped from her horse.

Using the momentum, she spun vertically

One, two, three turns, Qing finally extended her leg.

Her heel slammed into the bandit leader's skull with pinpoint accuracy.

Crunch. The hardest bone in the body met the softest organs.

Tap. Qing landed lightly.

Beside her, the bandits leader finally drew his sword in panic.

Qing tapped his chin with her left fist, then delivered a swift kick between his legs.

His eyes rolled back as he flew back.

Her flew away in silence while foaming at his mouth.

Thud-thud-thud!

Meanwhile Lu Bu circled back to Qing.

She leaped and landed onto his back.

It was not fancy horsemanship, just pure physical prowess met by Lu Bu's clever deceleration.

Back in the saddle, Qing approached the carriage blocking the road an pulled Lu Bu's rein to slow it down.

Heeiin! Lu Bu reared again, Moonlight Sword rising even higher, its blue Sword Qi scattering like icy starlight.

The men, who were trying to calm the panicked horse that dragged the carriage, turned pale at the sight.

Qing tossed out a line.

"What're you doing? Why are you not running away? Want an encore? Here, look, twinkle twinkle. That's not drool."

Heeiin! Lu Bu neighed in agreement.

But the bandits leader who previously taunting now frantically waved his hands.

"W-Wait! Great Hero! This is all a misunderstanding, misunderstanding!"

"Misunderstanding? What misunderstanding?"

"We just wanted to ask for help—"

"Oh? Then what was that about ‘men and women having fun together'? Sounded like some pretty serious harassment to me. Was that a misunderstanding too?"

"Th-That was, uh, just a game of shuangliu! It's a lonely road, so let’s pass the time playing shuang liu, that’s what it meant!"

Shuangliu\footnote{雙六; lit. 'double six'} was a dice game where players bet on the outcome of two rolled dice.

"Shuangliu? How much shuangliu have you done to make the number that red? Whatever."

"Huh?"

"Talking about games is boring. Here we have a chivalrous hero and some bandit scum, wouldn’t there be something fun to do together??"

Qing grinned brightly.

"Run. Fast."

\vskip
\begin{lstlisting}
     The chapter title is a reference to 1924's Korean short story 'One Lucky Day'
\end{lstlisting}