\chapter{One Lucky Day (3)}

Qing's mood as she set off toward Mount Changbai after breakfast at the inn was as lively and cheerful as ever.

Because the streak of good luck that had followed her all day yesterday seemed poised to continue today.

\textit{Look, there are already people tailing me.}

\textit{Am I going to have a blast right from the morning??}

Sure enough, Qing's sharp senses picked up a group of suspicious figures following her.

After all, ordinary travelers or merchants wouldn't have any reason to trail her like this.

It would've been more natural to quickly catch up and suggest to join them, saying things like 'How far are you going? Want to travel together? We'll treat you to a meal!' .

The fact that they were keeping their distance and following her meant they definitely didn't have good intentions.

Qing patted Lu Bu's neck affectionately.

\textit{What a clever boy. Our Lu Bu's mere presence alone has the talent to provokes and luring bandits out of the woodwork.}

About half a a \textit{shichen} after leaving Fushun County, a large lake stretched out to their right.

It was called Jeongwol Lake\footnote{most likely what is now the modern Dahuofang reservoir}, frozen solid in the bitter cold of Liaoning, casting a desolate yet serene landscape.

Following the frozen lakeshore you would eventually reached a fork in the road, one path leading toward Manchuria, and the other toward Huanren County.

\textit{Oh, looks like the bandits decided to make their move here.}

Qing smiled faintly as she spotted a figure standing motionless at the fork.

They were far enough from the city, about half a \textit{shichen} ride, to be in a secluded mountain path.

If they went any farther, the bandits would have too long a journey back home after their business.

So this was the perfect spot for them to reveal their true colors.

Suppressing her excitement, Qing slowed her horse's pace and approached leisurely.

The figure at the fork was a man and a woman.

The woman was unremarkable, but the man was quite striking.

He carried multiple swords on his waist, and long spear shafts protruded from his back, giving the impression of a walking arsenal.

You could say it looks like it's going to be a one man army.

But then again, was it really necessary to go through the hassle of carrying around so many different types of weapons?

If you weren't picky, you could just grab whatever was handy, so there was no need to carry them all at once.

Mastering even one weapon was hard enough, so how could you become an expert by imitating octopus?

\textit{Still, judging by his appearance his alias was probably something like 'Ten Weapons Ghost.'}

\textit{Depending on his level, it might evolve into 'Hundred Weapons Ghost' or even 'Ten Thousand Weapons Ghost' if he ever made a name for himself.}

Qing was brimming with confidence.

Here she was, casually analyzing her opponent like she got all the time in the world.

But why wouldn't she be confident?

She was a master of the Harmony Realm—no not just any master but a transcendent one bordering on the Profound Realm (not really).

Against a Harmony Realm opponent, she had nothing to worry about.

\textit{It's not like a Profound Realm expert would just pop up out of nowhere right?}

Qing suppressed the killing intent threatening to spill out.

\textit{Delicious breakfast! A strong invigorating start to the day!}

\textit{Strength calls for blood!}

\textit{And I'm feeling pumped!}

Qing approached the pair with excited mood.

When she stopped in front of them, she couldn't help but wonder what nonsense they'd spout this time.

\textit{What'll it be? The usual 'spare me' spiel? Is that damn wine-vinegar thingie making a comeback? Or maybe 'my leg hurts your horse looks nice'? Or will they surprise me with something creative?}

And indeed what came next was completely unexpected.

"Heavenly Blossom Sword, is it?"

Qing froze. They're looking for her all of sudden?

"…Who are you?"

"No need to be so wary. A Harmony Realm master hiding her face, and carrying a big sword, so it must be Three Heads…ahem my apologies, that's no way to speak to a lady. So I just assumed you must be the Heavenly Flower Sword."

"Gasp!"

That wasn't Qing.

The woman beside the man who had been standing there blankly was greatly surprised.

"Heavenly Blossom Sword? Are you really Heavenly Blossom Sword? Wow, I never thought I'd see the real thing. This is amazing."

She bowed deeply.

"I'm Gong Ryang Sayun. I thoroughly enjoyed the sight of your hearty meal. I too, pride myself on my appetite, but I was deeply enlightened by the knowledge of the heavens above. Please call me Sayun, a junior who walked the same culinary path."

Regardless of the woman's reaction, Qing's heart sank.

\textit{They didn't found I am Ximen Qing first, a Harmony Realm master.}

\textit{Rather, they knew I'm a Harmony Realm master, then working it back by my characteristics, found out my identity.}

\textit{In other words, they already knew my realm.}

\textit{When did they knew?}

\textit{I didn't even reveal my mental imagery yesterday, just Sword Qi. So how did they know I'm not in Peak Realm, but confidently guess Harmony Realm?}

\textit{Meaning they could tell my cultivation level at a glance.}

\textit{How's that even possible?}

"By any chance, are you… a Profound Realm master?"

Qing had always followed the principle of 'strong to the weak, weak to the strong'.

She was always cringing before the strong and proud before the weak. A petty person who's shameful no matter where she was!

So her attitude instantly became deferential.

"I am in the Profound Realm, but I wouldn't call myself a master."

\textit{What kind of nonsense is that?}

\textit{If a Profound Realm expert isn't a master, then who is?}

\textit{That's like a CEO of a megacorp saying 'I'm the CEO, but I'm not rich.'}

"I reached the Profound Realm over ten years ago. And in all that time I haven't made a progress. How could I call myself a master?"

"Ah, I see."

"Sometimes I wonder if I'm even in the Profound Realm at all. Maybe I should've entered Demonic Ascent first before reaching Profound Realm? But they say breaking off from Demonic Ascent and entering Mid-Stage Profound Realm is several time more difficult."

Suddenly the mood turned into a pity party.

Qing, still cowering internally listened quietly, to his lament.

"I thought the same. Breaking into the Profound Realm felt too easy. But once I got here, I couldn't move forward at all."

\textit{Well, isn't that normal?}

\textit{Even within the same realm there are Early, Middle and Late Stages, but the gap in the Profound Realm is so vast that such classifications become meaningless.}

\textit{Even Master said that advancing even a single step in the Profound Realm is harder than all the training that came before it.}

"So, after much deliberation, I concluded that I should collect as many martial arts as possible. That's why I've been traveling to learn them."

Qing gulped.

\textit{That's… a weird conclusion. Or rather, the conclusion isn't weird, but the method is questionable.}

"Um, when you say you've been traveling to learn martial arts… do you mean what I think you mean? Most martial artists won't teach outsiders. Especially those from sects, they'd rather die than leak their techniques."

"I thought they were just bluffing, but surprisingly, they really chose death. Still, in the end they taught me their martial art quietly, and I let them live. That's why rumors about me, Plunder Demon, started to spread."

Qing's expression turned completely rotten.

\textit{Damn it.}

\textit{I thought he was just a horse thief, but he's a martial arts robber.}

\textit{And a Profound Realm one at that.}

\textit{What kind of Profound Realm expert goes around robbing people?}

\textit{Does it even make sense to run into a Profound Realm master on the street!}

Qing felt wronged.

Of course, the whole situation was really unfair.

Profound Realm experts weren't the kind of people you just bump into!

There are only nine officially recognized Profound Realm masters in Wulin, though unofficially there might be more.

But still, in this vast Zhongyuan, there were only nine confirmed Profound Realm masters. Meeting one in the wild was practically a once-in-a-lifetime event.

Sure, she'd encountered one at the Imperial Palace, but that was the palace, it made sense for a Profound Realm expert to be there.

But here on a random mountain path, a Profound Realm master pops up demanding martial arts?

Unthinkable.

And yet it was happening.

"I have other names, but since now I'm a robber, them I'm Plunder Demon."

And who was Qing?

A martial arts thief who stole techniques through her mysterious Status Window, leaving her victims none the wiser, a phantom thief of martial arts, and in fact the candidate for the Divine Thief title herself.

So this was a dramatic encounter between a martial arts thief and a martial arts robber.

Perhaps it was a fated encounter.

"Don't take it too badly. I'm desperate too. I do have some shame, so I'm giving you a fair chance to fight back. It's a bit stretch to say it's the payment for your martial arts, but sparring with a Profound Realm master is a valuable experience, isn't it?"

If he had any shame in the first place, he wouldn't be robbing people of their martial arts.

Still, it was true that fighting a Profound Realm master was an invaluable opportunity.

Especially since they could go all out, in order to survive and protect their martial arts.

The last shred of the Looting Demon's conscience, a faint triangular trace could be seen rising above the circular worn-down conscience.

Not that it made him any less shameless.

Who in their right mind would betray their sect and master just to survive?

So Qing put on a solemn expression—

\textit{Hmm, which martial art should I hand over?}

\textit{The Yin Jade Maiden Divine Art that turns a handsome man into a beautiful woman would be appropriate, but um, should I ask permission from Xue Ganom for that?}

\textit{Of course, if it were Xue Ganom, he would say that there was no need to worry about making enemy with his sect, since he already wiped out them himself.}

\textit{No, if I do that, I might end up incurring a grudge a Profound Realm master…}

As Qing hesitated, the Looting Demon grew impatient.

"Come on, what's the point of stalling? Now, what weapon should I use? Sword? Spear? Saber? Halberd? Staff? Since you use a sword, I could match you with one. Or, you could pick a weapon you've never fought before. Anything will do. What'll it be?"

That last part caught her attention.

Qing quickly replied.

"Then, how about fists?"

Plunder Demon's eyebrows twitched.

"Don't you have any shame? Fists? I've never even learned such a crude skill. Who'd fight barehanded when they have weapons?"

"But you said I could choose anything."

"I said choose a weapon. If I wanted to fight barehanded, why would I bother carrying all this?"

"Still, fist techniques are the purest form of martial study that explores the most fundamental aspects of human nature, and in that sense—"

"Enough with the nonsense. You just picked fists because you think it's the easiest option."

Qing grumbled internally.

\textit{Damn it, that didn't work.}