\chapter{One Lucky Day (7)}

There was a minor incident, but it was ultimately resolved amicably.

But.

The fact that a Profound Realm master suddenly appeared while she was walking down the street left a deep sense of unease in Qing's heart.

\textit{No, no matter how continental the climate is, even if it's Zhongyuan, a vast landmass filled with countless people, isn't it crossing the line for such a master to rain down without any warning?}

Of course, the Profound Realm master might think that's unfair.

Even a Profound Realm master was a martial artis, not a tree that has just taken root in one place, so of course he could wandering around.

From a Profound Realm's perspective, all the people they passed by while walking around were just people who suddenly encounter Profound Realm's master.

\textit{If you look at it that way, it's not unreasonable, but, um, definitely, this isn't right.}

\textit{Either quickly rise to Profound Realm and walk confidently anywhere in front of everyone, or I'll need some kind of method to deal with a Profound Realm master.}

\textit{As things stand now, even though my opponent is giving me a break, she's unable to defeat him.}

\textit{If I open my mouth and make him angry, if I make him lose his senses, I might be able to get out of his way, but then I'd be putting myself in danger too…}

\textit{Strength! I need more strength!}

\textit{I need overwhelming power!}

Qing yearned for strength again.

\textit{It's not like I desperately want some kind of power, so I don't hear a needlessly serious voice saying, "Do you need power?'}\footnote{typical shounen cliche}

\textit{The completion of Nine Swords of Solitude is postponed indefinitely due to Heavenly Martial Emperor gramps's tantrum.}

\textit{But, it is not like I can suddenly reach Profound Realm by doing special training like closed-door meditation or physical exercise.}

\textit{So, the only way to gain strength right now, to strengthen my power, is to gather all of Ten Great Demonic Arts Under Heaven.}

\textit{It wasn't that far off.}

\textit{Once I collect the Pacheonyeokhyeol or whatever, I should be able to exchange the accumulated Good Karma at least twice.}

\textit{It's probably possible to do it three times, but the problem is, there are no guarantees.}

\textit{If I exchange it carelessly and it gets stuck at the second attempt, um.}

\textit{Compared to finding one of the three remaining Ten Great Demonic Arts, finding the last remaining one would be a task that is three times more difficult, even if you just look at the numbers.}

\textit{It's probably not three times as likely, not that I ever like math in my previous life.}

\textit{Of course, if it's a waste of time this time, I can just exchange it for now, and if I don't have enough karma, I can replenish it by hunting up bad guys.}

If I had to say, this is an all-out war, a total war to gather Ten Great Demonic Art Under Heaven.

Qing's determination was rekindled anew.

\textit{There is no time to be like this.}

I have to thoroughly search Mount Changbai right away.

"Lu Bu, come here. Let's go."

Qing called out to Lu Bu, who is standing next to Plunder Demon, who was snorting and whining, and who had been teasing Plunder Demon for a while.

\textit{No, why is it doing that over there again?}

Hiieeng!

At Qing's call, Lu Bu responded with a loud cry and rubbed his nose on Plunder Demon's shoulder as if to show off.

"Haha, what a charming horse! Judging by its appearance, there's no other fiercer horse in the world."

"Lu Bu?"

Hiieeng! Lu Bu cried again as he looked at Qing.

Even though Qing was fluent in all human languages, she didn't have the ability to understand the cries of animals.

With his head standing stiffly and the whites of his eyes shining brightly, adding to Lu Bu's gaze looking down, it somehow sounded like this to Qing.

'I don't listen to the weaker ones!'

That's not all.

Lu Bu knelt down next to Plunder Demon.

Horses were animals that naturally feel most comfortable standing on all fours, so there was only one reason for them to kneel and lower their bodies.

'Hurry up, human. Run with me.'

"Huh."

Suddenly, Murong Jun's young voice seemed to come into Qing's mind.

-There are guys like this, leader horse? They're sensitive to their master's authority (omitted)

\textit{Come to think of it, wasn't it Lu Bu who came to me without any hesitation and acted cute as soon as his master died, without any mourning at all?}

\textit{Now he is flirting with Plunder Demon and hitting on him.}

As befitting the name Lu Bu, it seems that he already wanted to welcome his third official master.

Judging from the amount of care been done to him, there must have been several owners before, but when Qing named him Lu Bu, at least the owners were that barbarian and herself.

The veins on Qing's forehead flared.

\textit{No, this bastard? Just because I lost once, he didn't look back and changed his owner all at once?}

"Lu Bu, you little shit, aren't you coming?"

-Hieeng!

"We're done. Tonight's dinner is horse meat. I heard horse sashimi\footnote{馬刺し; basashi} is so delicious. You should know that today is a day when both of us will burst."

-Hieeng!

Then Lu Bu hid behind Plunder Demon.

Horses were basically large animals, so hiding behind Plunder Demon didn't make him disappeared.

\textit{No, this guy is really funny, isn't he?}

\textit{He immediately betrays as soon as he's given a chance, and as soon as he sees a better master, he immediately changes his master. His personality, no, his devilish nature is impressive.}

\textit{Before that, that confidence.}

\textit{His baseless self-assurance, believing that if he changes masters, they'll unconditionally accept him, is laughable.}

\textit{Well, seeing as how everyone who saw Lu Bu was talking about the Thousand-Li Horse and all that, who would give up on a famous horse that rolled into their hands?}

Qing was pin-pricked.

Qing glared at Lu Bu fiercely.

But that was all.

Because, according to the strong-weak nature, she couldn't confidently make the request to Plunder Demon.

So, the best thing that Qing could do was to keep her mouth shut and pretend to be pitiful.

It was actually the best move.

'Sir, it seems that Lu Bu is trying to make you his master. That's absurd. Could you please send him this way?'

If she said so, would he send Lu Bu back?

Wouldn't a martial arts robber, who stole other people's martial arts. not steal it?

Rather, he'll giggle and try to take it away, saying, 'You're following me as your master?'

But if you just keep your mouth shut, other people will think you're just being cute.

\textit{If I just sit there and don't say anything-}

"Lord Plunder Demon, it seems this beast has changed masters. Indeed, the behavior of a mute, insignificant creature."

The Gongryangsa Yoon who was next to him immediately struck the target.

At that, Plunder Demon just sighed.

"I already have a horse to ride. But I can't just turn away a beast that came to me on its own."

"Then, shall we have horse meat for dinner tonight?"

"No, it's obvious that it's a fine horse, why would you eat it?"

"Aren't you curious? I'm very, very curious about whether a fine horse truly lives up to its reputation. Surely no one has ever eaten a fine horse? Besides, it's a freeloader, so there's no need to feel sorry about it, right?"

"Hmm, well, that's true. If a horse changes hands so easily, it'll probably just leave when it finds someone it likes better. In that case, maybe it wouldn't be a bad idea to eat a full meal."

"Gulp."

"Well, there will be a lot of meat."

At that, Lu Bu showed off his magical ability of walking sideways with a clattering gait and a panicked cry, and moved away from the two people.

And then, very naturally, he came up to Qing and rubbed his nose as if nothing had happened.

"What, aren't you going over there? I'm going to go and get a lot of the horse meat when they have a big feast."

Hee-ing! Yeo-bu cried out in frustration and looked around, his mane stood up.

Those eyes were exactly like the eyes of a pet dog that has been in trouble and were looking for its owner.

Qing bowed her head slightly to Plunder Demon with a sour expression.

Well, even if you say you're going to eat them, horses were basically expensive property, so if you take them and sell them, you can enjoy a horse meat festival week for two months, rather than a horse meat feast.

Since he just pretended not to know and sent it away, it was only natural that she should express some gratitude for it.

"Gulp. That's too bad. If Heavenly Blossom Sword ever to have appetite for that beast, please let me know."

However, Gongryang Sa-yoon seemed to be very sincere, and could not hide the gleam in her eyes, causing Lu Bu's voice to tremble.

Anyway.

Qing climbed onto Lu Bu's back.

Sitting on the top of Lu Bu, she nudged its torso with her thigh in annoyance, and it let out a sigh of annoyance and looked at the distant mountains.

\textit{Anyway, I thought I was starting to like this bastard Lu Bu, but I've completely lost it.}

"Ugh, let's go."

When Qing lightly pulled down the reins, Lu Bu walked away quietly like a docile lamb.

It was a truly smooth and elegant maneuver, not the terrifying ride of bouncing up and down with the rough gait of the past.

\textit{No, this kid, you can even walk like this? Hey kid, there's no special food for the time being. Just eat some tasteless grass and reflect on it.}

\textit{And so, let's start again.}

\textit{…why are you?}

Qing asked with a very, very bitter expression.

"Hey?"

"Hmm? What's wrong?"

"Were you also on your way to Huanren County? Then, should I take a different route?"

"Ah, you were on your way to Huanren County?"

"Oh, then, where are you going?"

"Where are you going? I'll follow you."

Plunder Demon answered calmly.

Unfortunately, the content was not calm.

Qing's expression darkened.

"No, what are you following me for? We're supposed to meet in a month, don't we."

"The training is only a month away, but you never said we shouldn't go with you, did you?"

"No, isn't this against the spirit of the agreement? Then I can't go anywhere if you follow me around. What, if I were to head to Wulin Alliance, you're going to tie me up and lock me up somewhere?"

"I'm not that incompetent. Besides, since you're the Heavenly Blossom Sword, your fame will spread everywhere. Even if it's a hassle to find you, it's not impossible, right?"

"But why are you following me around? No, you're a freeloading elder? Don't you have anything to do? Are you someone who drinks all day? No, you're not even freeloading, so why are you following me around?"

By the standards of Qing's hometown, it was an outrageous outburst of abuse, even for she called him 'elder'.

Actually, Zhongyuan's standard was the same.

But Plunder Demon just laughed.

Well, Qing already succeeded in reading the line, so it was okay to be bratty to this extent.

"I'm busy, too. I have an immediate mission to attend to, right? Hey, wasn't that a pretty important mission?"

"Absolutely, absolutely. That's what I heard."

Gongryang Sa-yoon answered.

Then the robber nodded.

"Did you hear? I'm such a busy person."

"No, you have work to do, and it's important work, so why are you following me?"

Qing asked again, astonished. Plunder Demon seemed to be talking nonsense.

"Has it been five years since I seeked martial arts? I've met countless martial artists, and aside of the common, widely known martial arts, how many truly proper technique have I acquired?"

"How many?"

"One. It's the one you taught me."

\textit{Shit.}

Qing's expression turned sour.

\textit{Five years of robbery and barely managed to acquire a single red-bordered martial art? That I was the first to offer it?}

Of course she was shocked and her eyes rolling in confusion.

"Collecting martial arts isn't as easy as you think. Those who open their mouths so easily were usually just mediocre ones who've mastered some common martial arts. Those with real martial arts never opened their mouths. Even if they do, they tried to give fake Sutras."

Suddenly, the atmosphere is filled with complaints and grievances.

\textit{But isn't that just Plunder Demon's situation?}

"So?"

"Aren't you going to Manchuria?"

"Uh, so what?"

"If you pass Changbai Mountain, you're either in Goryeo or Manchuria."

Goryeo disappeared a long time ago, and the current country name was Joseon.

To the people of Zhongyuan, the center of the world, it didn't really matter whether the barbarians in the east were called Dongyi, Goryeo, or Joseon.

Even for the Qing, this place was a pseudo-Zhongyuan anyway, and it was not even her Joseon anyway, so she had no obligation to correct the name.

"Goryeo doesn't matter, but there's a certain nasty master in Manchuria. He's a level, no, two levels better than me, and as far as I know, he harbors a considerable grudge against you."

"Hgg."

Qing was surprised.

\textit{If he's one or two steps better than Plunder Demon, then he's also a Profound Realm master. Why would that master holds a grudge against me?}

"No, why? I don't even know who he is, and what did I even do? No, who is that expert in the first place?"

"I can't say that. I have my own circumstances. Anyway, given the circumstances, if you go to Manchuria and suddenly die, what will happen to my martial arts?"

\textit{No, why is my martial arts called 'my martial arts'?}

\textit{My martial arts are mine, and umm, some of them are Shaolin's and some are Nan-gong's, so the ownership is a bit mixed up.}

Anyway, Qing's attitude softened a bit.

\textit{There's a Profound Realm master in Manchuria, in Jilin, who hates me. If I die, the martial arts he entrusted to me will disappear, so he said he'd go with me and mediate—}

"No, mediation won't work. I told you. He's a foul-tempered man. He'll never let go of his grudge. If we ever run into each other, I'll hold him back, so run away."

\textit{It's not mediation, it's letting me run away.}

Qing had to say something

"Um. Oh, thank you?"

Qing expressed her ambiguous gratitude.

\textit{In any case, isn't it true that he followed me because he said he would protect me? And he's even abandoning his mission to follow me, unconditionally and without fail.}

\textit{Of course, this part is a bit less reliable.}

\textit{He'd abandon his most important mission and come along just to steal some martial arts lessons. It made me wonder if a master of Profound Realm caliber really needed a new martial arts technique so desperately.}

\textit{But just looking at Heavenly Martial Emperor, he was completely obsessed with martial arts.}

\textit{If you think of it as a choice between duties and personal self-fulfillment, it's not to the point where it's not understandable.}

\textit{Anyway, thinking about it this way, it didn't seem like a bad idea for the martial arts thugs to follow.}

Like that, with 'cancers' attached to her left and right.

Journey to Changbai started again.
