\chapter{Every Treasure Has a Sad Legend (3)}

The Shandong Peninsula was often called the land that plunges into the sea.

This peninsula, which actually looks like the continent extending its hand into the sea, has a unique feature: a large rocky mountain along the way.

It's Mount Lao.

And there was a small port town below Mt. Mount Lao, Qingdao.

In Qing's hometown, you would be in the very town that's famous for its beer.

Beer brewed with the clean water of Mount Lao seemed to captivate the world, but later on, it became famous for something other than its taste.\footnote{An incident where a worker of Tsingtao brewery, based in Qingdao, caught on camera urinating into a beer tank.}

Anyway, Qingdao was a very small rural area.

"Huh? Qingdao was in the countryside?"

"Of course? You thought it's a big city? Well, I guess we could stop by to taste the water from Mount Lao, since they say it's medicinal."

"Uhh, isn't it famous for its maijiu\footnote{麥酒; lit. 'wheat alcohol drink'; beer}? Oh. Maijiu. I see."

Qing, who was good at thinking about food, quickly realized her error.

\textit{Come to think of it, beer isn't a Chinese liquor.}

\textit{Oing? How did Qingdao become famous for its beer?}

Of course, there might be a story about colonialism and its related issues in the future.

Those beer-loving guys who drink beer instead of water and have beer flowing instead of blood are illegally occupying the place and doing this and that and stuff.\footnote{Germany-occupied Jiaozhou Bay Concession}

But anyway, Qing didn't know and didn't really care, and it hasn't even happened in Zhongyuan yet.

So, whatever, it's fine.

Isn't the important thing the present purpose?

What was the reason for coming to this end of the continent, which was the most seaward part of Zhongyuan?

That's right, grilled clams!

It's to eat grilled clams!

\textit{It's not that I particularly want to eat it, but it's a precious food that holds the memories of Changming'er. Yeah. Yeah.}

So, she quickly secured a spot in the best guest room overlooking the sea.

Since they said there was only one special room left, they quickly grabbed one and put their luggage down.

Even when they entered the village of Jimo, the rain that had been falling in a drizzle as if sprayed by a sprayer began to pour down in earnest as the sun began to set.

Well, it's late August.

It was a leap year in winter, so summer was just ending, but it's now a time when it rained half the month in the Shandong Peninsula.

The best inn had a top-class restaurant that also serves as a bar.

\textit{Ah, the atmosphere is nice.}

\textit{Scallops and large clams—are these blood clams?}

A heap of small clams was also piled high on a large platter.

There, at the recommendation of the server, there are braised chicken\footnote{黄焖鸡;Huang Menji} with vinegar sauce\footnote{汤醋;Tangcu}, and short ribs with rice\footnote{(排骨米饭; Paigu Mifan}. There are also dishes whose names are completely unknown.

"Oh?"

\textit{I didn't have high expectations for the dish, as it felt like a side dish to grilled clams.}

\textit{What's this? This familiar taste? It's just right for my taste?}

Of course, there was no food in the world that does not suit Qing's taste.

\textit{But somehow, I have to say that it suits my taste better than other local foods.}

A large woman and a small girl were busy scooping up food with their hands. An old man sipped his drink, watching the scene.

So, on a summer night, the rain poured down and the sound of water falling was heard.

Thanks to that, the taste of a delicacy can be enjoyed while looking out at the night sea on a cool night.

"Ha, it's good to be out. Right?"

"Huh."

"No, Master. Why do you keep pouring the drinks yourself?"

"You're so busy eating that I can't even see your hands. Why bother pouring me a drink when you look so busy?"

"Hey, no matter how busy I am, there's always time to fill your glass. Now, please accept the drink offered by your disciple."

Gulp, gulp, gulp, the poured alcohol made a silky sound as she called, "Server, please give me the best liquor."

Tian Yuxue's expression as he grumbled but accepted the drink that Qing offered was incredibly warm.

So, Tian Yuxue can enjoyed the scenery with peace of mind and comfort.

It was a truly content life, not as poor as when he was in Anhui, but with an abundance of gold and silver.

Then, Tian Yuxue, who was naturally searching his memory for a fitting poem, suddenly had a question.

\textit{It's been a long time since I've felt so relaxed and happy, why?}

\textit{Well, it was a repetitive process of giving lectures in the morning, looking at maps from the afternoon until night, and then going to bed.}

\textit{It took quite a while too.}

\textit{I don't know why I've been so busy.}

\textit{It would be truly wonderful to just enjoy a small banquet together like this.}

\textit{Why did I had to come all the way to this distant land of Shandong just to realize this?}

\textit{If I had known sooner, we could have had a lot more fun together in Taiyuan…wait…}

"…?"

"Oh, is the bottle empty? Would you like another one? Here—"

"No, I'm done drinking."

Come to think of it, they didn't come here to play.

Qing led the group so naturally that Tian Yuxue also became intoxicated by the atmosphere.

'What is this? Why are you wasting your time and energy while we're on the noble mission of eradicating that vicious, evil Demonic Art?'

Tian Yuxue was about to pour out those words.

But what could he say in a restaurant full of people?

'You're supposed to be looking for treasure, but you're just sitting here like this?'. Even if you're not spreading rumors all over the neighborhood that you're here to find treasure, there's already a lot of people listening in…

Suddenly, Tian Yuxue was like, 'Oh my'.

\textit{Eavesdropping? Why didn't I notice it sooner?}

Actually, there are not many tables like this where people laughed and chatted like this at this luxurious table.

More than half of the people were quietly eating and drinking, looking around at what others thought.

Why was the restaurant full in the first place?

It's the Shandong Peninsula in August.

August was the worst time for tourists to climb Mount Lao.

The heat was at its peak, the sky was cloudy and it rains continuously.

If you were unlucky, a very strong wind and rain might blow, making it extremely difficult and dangerous to cruise.

Fortunately, his quick-witted disciple noticed this in advance and pretended to be a very wealthy tourist.

Tian Yuxue hid his serious feelings and smiled brightly.

"No, when will I ever get to drink a proper Laojiao\footnote{a distilled rice-based liquor brand, established in 1573, it's the oldest continuously producing baijiu distillery in the world} in Jimo? Order more."

"That's right. Here, Server, add one more bottle of Laojiao, no, two more bottles!"

"Yes! (fwwwwwwp) TWO MORE BOTTLES OF LAOJIAO!!!"

The excited server screamed so loudly that the entire guest room shook.

When it comes to Laojiao, it's one of the most famous liquors not only in Shandong but also in the entire Zhongyuan, and it's also an expensive liquor.

Of course, just as like in the other regions, you couldn't just ordered Laojiao just because you have some golds, but even if you have a fairly thick purse, it's not something you can easily order.

The crowd looked at the table covered with shells like a mountain, half with envy, half with jealousy, and swallowing their saliva.

It was a tower of shells that looked like a shell mound built by primitive humans.\footnote{Shell midden}

As soon as the Laojiao arrived, Qing, who has brought great happiness to the innkeeper and the guests, finally finished a sumptuous meal and went up to the best room at the top floor.

"Oh my gosh, my stomach is going to explode."

"Me too."

As soon as she arrived, Qing stretched out her arms and legs on the bed and lays down.

Not to be outdone, Chen Changming also lies down next to her in the same position.

Chen Changming, who was so small that she looked like she was about ten or eleven when they first met, was still the same little kid she was back then, as if she missed her growth spurt.

Lying next to a large woman, the difference in length was so great that they looked like mother and daughter.

"You fool, you should eat in moderation. Your stomach is four times taller than Mount Lao."

"Hey, it's a rare opportunity, so what? I was trying to be mindful of others in Taiyuan, so I barely ate anything."

The shocking fact was that when others eat one bowl, the three bowls she ate was a small amount!

It was a sound that would make all the scholars wondered, 'Where on earth did all that food go?', and blushed as they realized where it went.

"Anyway. You managed to catch on. Ha, it looks like things are about to get tricky."

"Huh?"

That expression on Qing's face.

Tian Yuxue realized his mistake.

\textit{Haiyaa!}

\textit{This girl just ate and played without thinking!}

\textit{It wasn't that the city crowds were unusual, so she pretended to be a tourist, but that she had no interest in hunting the Secret Manual in the first place!}

Tian Yuxue sighed deeply.

If he hadn't known she was this kind of girl in the first place, he wouldn't have noticed.

Tian Yuxue now knows that his disciple was a beautiful and smooth woman, not only in her skin but also in her brain, without a single wrinkle.

Perhaps, if he opened her head, her brain would be the most beautiful in the world.

Or, judging by her constant lack of thought, there might be no brain at all!

So, why not explain it to her?

"It seems there are several copies of the treasure map. Well, if there's one copy, it wouldn't be strange if there were two or three copies."

"What does that mean?"

"This is a truly brutal time to climb Mount Lao. It's scorching hot when the sun rises, and since it's a rocky mountain, there's nowhere to hide. And if it rains, even if you climb Mount Lao, you couldn't see anything."

"Ah. So it's not peak season now."

It's his first time hearing about the term 'peak season' but as soon as he heard it, he thought it was really fitting.

A season when there are many people who want to climb?

What an exquisite expression.

His disciple seemed to have no thoughts at all, yet she occasionally showed poetic talent—no, that's not the point.

"This is how the treasure search works. If there are multiple maps, problems like this are bound to arise. It wouldn't matter if all the maps owners were competent and reserved, but what if one of them was a loose talker or lacks ability?"

A man who was too talkative to show off the treasures he has in his possession will eventually let the words leak out.

Still, it's better to be open-mouthed.

If someone lacked the ability to find the treasuse, they'd just sell the map.

Would a merchant want to receive only one customer?

"You're saying that in this expensive inn, the only rooms left are the best ones? You're saying that the water has been rising from below, leaving only floor the top empty?"

"Whoa, what's going on? Aren't you saying the whole city was teeming with treasure seekers?"

"Yeah. It would be fortunate if they didn't know what the treasure is."

Tian Yuxue trailed off.

Those who came looking for some great treasure like gold or silver, and those who came looking for the worst kind of Demonic Art like the Killing Among Killing had completely different mindsets.

Why would Divine Thief steal treasure?

Certain types of treasures were bound to bring about a storm of blood in Jianghu, such as famous Divine weapons, Divine Arts, or vicious Demonic Arts.

What if it's the Essence Absoption?

Only then did Qing's expression become serious.

\textit{I thought I would just have to climb the mountain, suffer a bit, find the hidden spot, and burn the manual.}

"Then what should we do? Should we secretly find it and get rid of it? Should we go find it right now?"

"Ha. Are you talking about climbing a mountain in the middle of a rainy night? You have to see to find something, or else you won't find it."

On a moonless night, even with Qing's eyes that transcend human eyes, nothing can be seen.

According to scientific principles, in order to see an object, there must be a light source that reflects off the object and enters the eye.

Of course, whether you know the scientific principles or not, anyone would think that you can't see if there's no light.

"Then?"

"We must prepare thoroughly and sneak in quietly at dawn. We must stay in the mountains, search quietly, and then sneak out. Otherwise, there will be chaos."

Qing's face expression was getting rotten.

\textit{Isn't it a story about going into the mountains, eating, sleeping, and camping out to find treasure?}

\textit{No, I thought I could climb the mountain when the sun rose and come down when the sun set to rest.}

How could it be that easy?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

So, Mount Lao!

The highest peak was less than 400 zhang high above sea level\footnote{about 1.2 km high}, so it's not a very high mountain by Zhongyuan standard, but the mountain that touches the sea was the same height as sea level, so it's actually a mountain of considerable height.

There was a rocky mountain there, and the peaks are all made of rocks and oddly shaped rocks, so it's actually a huge mountain with a great sense of imposing power.

And although Mount Lao was a solitary mountain rising alone amidst the surrounding sea and plains, it boasts a vast expanse of mountain scenery.

So, Mount Lao was wide.

It's very spacious.

According to the unique Korean measurement system, the area of ​​Mount Lao was equivalent to 154 times the area of ​​Yeouido.

That is, one hundred and fifty-four Yeoui Island.

For reference, this Korean weights and measures, Yeoui Island, was an official measurement used in official documents.

However, it has the disadvantage that even among the Korean people, nobody understands it properly.

So, if the Korean people heard-

"Mount Lao was about 154 Yeoui island."

When you say that, the Korean people couldn't imagine how wide that mountain is. They'd say, 'Hmm? Is it wide? I don't know'.

Instead, you should tell them, "It's 75\% of Seoul, or three-quarters of Seoul."

Then the Korean people would shout-

"Wow, what a vast mountain! You really have to search it? If I were you, I'd rather die than search through that place!"

This was precisely the feeling of Qing heading to Mount Lao.