\chapter{Every Treasure Has a Sad Legend (5)}

The man's name was Jang Bu-beom.

His original name was Jangbeom, but he didn't like the name Beom, which was given to him because he was told to only use the middle name wherever he went, so he changed it to Bubeom.

My hometown was a small village in a corner of Seorim-hyeon, and I have a family that I haven't seen in over ten years.

Fortunately, while working as a ronin, he was able to master the art of internal energy through a few lessons, and with that skill, he was able to enter the Tailong Sword School in Wuyi County, Guangxi Province.

"Tsk. Who said they were curious about my personal history? How, why, where did you come from?"

Tian Yuxue clicked his tongue.

It's a stereotypical self-introduction that starts with "I am someone from somewhere," but this was actually one of the ways to beg for one's life that has been passed down in the martial arts world, whether known or not.

There was a difference in the weight of killing an enemy whose name you don't know and whose origin you don't know, and killing someone who was from a certain place, has a certain family, and has lived a certain life.

Jang Bu-beom was startled by this and quickly blurted out everything he knew and didn't know.

"I participated in the martial arts competition last June. There, Dae-Hyeong obtained information that a great sacred treasure was sleeping in Laoshan on the Shandong Peninsula…"

"Martial Arts Competition? What martial arts competition? Was it the end of last year?"

"It's this year. Ah! This isn't the Jeongpa martial arts competition, it's the Heretic Alliance martial arts competition."

Tian Yuxue's expression became serious.

I don't really care if the Sapa guys are holding a martial arts competition or a sports day, but since the Sapa guys have their own unique bravado, they would have gathered as many people as possible.

"Information circulated at such a major event? Who the hell would leak such information? How openly was it circulated?"

"Well, I don't know. Dae-Hyeong found out, but I don't know. Thanks to that, I managed to sneak out during the martial arts competition…"

This was the reason why so many people dropped out during the Sadoyeon martial arts competition, but anyway, Qing and his party didn't even know that Sadoyeon was holding a martial arts competition.

Tian Yuxue's expression becomes serious.

"It was called Shingabibo. Do you know what that's?"

"There's something to be said for the large horse, and if my guess was correct, it must be some great miracle…"

"Ha. Right. I don't think that big guy told you. But you found the grave, right? Why?"

When we met, I thought it was nice to meet you, but didn't you ask if I knew of a graveyard or a suspicious cave?

It's a suspicious cave, so it's natural to ask, but I can't just pass up asking about the grave.

Because it's the new city and the new city.

That's what the clues in Jang Bo-do were like-

"They said that the Shingabibo was located at the place where the Shin clan tomb was located in Shinsi."

As expected, such a story comes out.

Tian Yuxue sighed deeply.

This guy Jang Bo-do was so loose-lipped that he's been blabbing to the whole world about something evil here.

Every time Tian Yuxue asked questions like how many other people had come, how many people seemed to have come looking for treasure, etc., he received a very broad answer.

Jang Bu-beom, who overheard the heinous conversation of the hemp heads, answered very obediently and meekly.

After that, Tian Yuxue's words become empty for a moment.

Jang Bu-beom's eyes just rolled around.

That was when.

"Have you asked everything you wanted to ask?"

"Well, yeah. I didn't really expect you to know much, but you know enough."

"Well then, please tell me how to break the danjeon without killing anyone. I also have some teaching materials that I can use to practice."

Jang Bu-beom, who was lost in thought, frantically moves his mouth.

The same old pleas like, "I told you everything I know," or "Please show mercy just this once."

Tian Yuxue cuts off his words with a "tsk" and looks at Qing with a crooked expression.

"What? A textbook? Are you calling that a word?"

Was the word choice a bit off?

Qing gives a cute smile to Baesishi.

"Hey, Master. Didn't you see him swing his sword so abruptly? He didn't hesitate a moment, and he's done it more than once or twice. It's not like he's going to lose anything by letting a few herbalists into the mountains. How could he possibly care so little about the lives of civilians?"

"Hmm."

At that, Tian Yuxue's expression softened.

"In Confucius's words, that guy was like someone who shits in the middle of the road. He's someone you can't even talk about."

Now that he has learned, he can even write letters.

As Confucius was walking along the road, he saw a man hiding in a corner of the road and defecating.

Confucius rebuked him -

Hey, you shameless bastard!

Then the guy who had been shitting blushed in embarrassment and asked for forgiveness.

However, considering that Confucius was a muscular giant of just under seven feet tall and a master of martial arts at the time, he would have asked for forgiveness even if he had no shame.

And as Confucius walks along the road again, this time a guy pooping in the middle of the road suddenly appears.

Confucius frowned, his eyes looked as if he was looking at the world's dirtiest thing, and he quietly turned away.

His disciples asked him, "Master, he's pooping right in the middle of the street, and you don't say anything? Is it okay for him to poop so confidently?"

Then Confucius answered.

A man who poops secretly on the side of the road knows that his act was shameful, so he poops secretly.

I only nagged because if you know your own shame, you can correct it by scolding yourself.

But the guy who fights in the middle of the street was a kid who doesn't understand, so there's no reason for him to talk so loudly that my mouth hurts.

It was impossible for Tian Yuxue to not know this basic anecdote.

This was a famous anecdote that's often told to children when teaching them about Confucianism because it's also fun.

"Emma. Even so, what's a teaching aid? Isn't that something only the world's greatest master would say?"

"Hehe. Are you going to teach me?"

Jang Bu-beom was startled and shouted at him.

"Wait a minute! Didn't I tell you everything?"

"Why? Don't you want to break your danjeon?"

"Oh my, you know this too, Grandmaster! To a warrior, dantian was more precious than life itself!"

"Really? Then I'll just kill you?"

"please……."

"Then you should have lived a good life. Just looking at you, you can tell just how much of a tyranny you've committed."

Qing looks at the number above Jang Bu-beom's head.

Yeah. This number isn't some absolute standard for killing or saving people.

But, you can use it as a reference, right?

"I will live well, well."

Qing bursts out laughing at him.

"Do you think I've heard that kind of thing before? That's why I'm trying to help you live a good life. Even though I'm a lame person who's lost my inner strength, I'm still not useless. Live honestly and earn the goodwill of others with your good intentions."

"Wait a minute, a limp? What does that mean, huh?"

Qing skillfully places the vine back into Jang Bu-beom's mouth.

The words of the sages I learned from Taiyuan are still just vaguely floating around.

Still, it's different from before when I didn't even want to think about it.

Okay, let's admit it.

Murder was simply a means of inflicting the most intense pain.

What I like was precisely the act of causing pain: frustration, despair, sadness, loss, etc.

Yeah, honestly. A perverted pleasure killer, that's right.

I don't know if it's because of the Thousand-Year-Old Fortress or the side effects of the magic, but it's really gone.

But, what to do with a head that has already lost its flavor?

So, I was cleaning up the trash and also satisfying my own selfish desires.

What's wrong with that?

Still, if you look at the events that occurred during the worst turbulent times of Zhongyuan, it's like this.

The lesson was that if you don't get rid of the bad guys, the good guys will eventually suffer.

The teachings of the Hundred Schools of Thought were ultimately a collection of conclusions reached by numerous thinkers on how to deal with bad guys.

The Legalists proposed establishing laws to determine the severity of crimes and to kill or torture them, while the Mingists worked to expose and improve the loopholes in the laws.

Confucius wants to create a social atmosphere that despises evil, so that people feel ashamed of doing bad things and cannot do them because they are afraid of losing face.

Sick leave was a powerful force! Let's start with unification.

Let's stop the war for now! Let's start with a peace treaty.

The Mohists believed that if everyone became everyone's acquaintance, evil would disappear.

Farmers said that the world would become peaceful if all non-producers, that's, those who earn unearned income, were euthanized.

Kings, nobles, and organized crime lords.

And the rental business operator (important).

Poetry and novels recorded the times.

The Yin-Yang scholars explored the world, saying that they had to first understand why the world was in chaos.

And the Taoist school of thought among the Hundred Schools of Thought, well, it's a bit strange for a Taoist to say this, but he seems like a retard.

Why aren't there kids like that?

Those who do nothing themselves but pick a fight over everything others do.

Because Taoists were just like that, they devoted all their energy to criticizing other thinkers of the Hundred Schools of Thought.

When asked what to do about it, everyone spouted out ridiculous nonsense like, "Just give up your greed and let it be" (inaction takes place naturally).

As a result, Taoism as an ideology declined and went into the mountains, becoming a religion and cultivation practice that was a friend of Buddhism. Taoism disappeared and Taoists remained.

Anyway, let me summarize the thoughts of the Hundred Schools of Thought in my own way.

okay.

It has always been people who judge people.

What qualifications do you have to eradicate evil?

Because anyone can clean up trash.

I guess this was why people have to learn.

In the past, when I thought about this, a corner of my heart would feel cold and I would feel vaguely guilty, so I just avoided it.

"Hmm. Like this? Hmm, it's leaking now?"

"Well, I've put the gold out there. Remember that vital energy leaking from the acupoint right now. Just think about gently breaking and cutting out that area, around the entrance and exit. If you're in a hurry, you can break anywhere, but it'll seriously damage your internal organs."

"Oh."

The Great Scholar was the head of the Hanlin Academy.

Below them are the co-leaders, Shiganghaksa and Shidokhaksa.

A scholar who teaches the best in the world was called a shi-gang-hak-sa, and a shi-dok-hak-sa means someone who has read the most books in the world.

Tian Yuxue was a scholar of poetry, and he has proven through all his teachings that he was truly qualified to be a scholar of poetry.

"Let's see. Hmm. It's been cleaned up nicely."

"lol."

In contrast to the warm atmosphere between the disciples, Jang Bu-beom, who had lost all the inner strength he had accumulated throughout his life, simply stared into space with cloudy eyes and shed tears.

Qing smiles at the sight.

Isn't that a really nice expression?

"Ah. Now I have some legs left. They hurt a little. Please bear with it."

The focus quickly returns to Jang Bu-beom's house.

"Whoosh!"

"Oh, don't move. If you sprain your ankle, you might end up with one leg instead of a limp. But you should still be able to walk."

"Whoohoo!"

However, in front of the overwhelming strength of the Ximen Qing, which turned the Xiang Yu General into a Southern Heavenly Flower, there was no way that a gangster who had been demoted to a third-rate level due to his inability to use his internal energy could resist.

Qing, a master of anatomy, skillfully removes the knee joint.

Surprisingly, the gagged mouth was quiet.

Because the pain of dislocation was so extreme that it doesn't even elicit a scream.

Because the pain seemed to be transmitted through the trembling muscles.

Wow, really. How much would it hurt? You must want to die, right?

I don't know how to live without this kind of fun.

After carefully twisting and cutting a single ligament, Qing puts the leg back together again.

Jang Bu-beom's body, which was trembling and almost on the verge of fainting (unfortunately, he couldn't faint due to the pain), sagged as if his energy had drained away.

"Okay. You can't put any pressure on your right foot anymore. Well, it's not like you can't do everyday things."

Qing asks with a smile.

"What do you think? Do you think that big guy would protect a younger brother with a cripple leg and no internal energy? Well, I know the loyalty of the Sapa kids well, but I think he'd end up being treated like a cripple and kicked out?"

A hostile gaze was fixed on Qing.

What was it? Why are your eyes so wide open?

But it's a reward for me. I like it.

"You won't be able to run with these legs, but if you come into my sights after this time, I'll kill you. And I won't kill you gently. I'll skin you and roll you in the sand until you beg me to kill you."

Originally, sincerity had a certain resonance that was unique to sincerity.

In addition, Qing was a person who does not hide his original expression.

Then, Jang Bu-beom's eyes, which were filled with poison, softened and sank downward.

I thought I would really die if I opened it.

The sound of his voice was so thrilling that it sends a shiver down my spine.

I think not killing them was also secretly okay?

So, was that why both the black guy and the guy who uses the sword in the opposite direction are immortal?

"Okay. Let's run away. Where did you say it was? The Taeryong Sword Sect? Wow, how did you memorize everything after hearing it once, Master? Anyway, don't even think about joining up with those Taeryong guys. You'll know if we catch you, right?"

Jang Bu-beom nods his head vigorously.

To him, Qing said, releasing the gag.

"Return to your homeland or settle down somewhere else. I won't go so far as to tell you to live a good life. Just don't live a bad life. After all, if you live a bad life with that body, you won't live long. What's a cripple fighting for? Just live your life thinking that if you take revenge, you'll die, and be mindful of what others think."