\chapter{Every Treasure Has a Sad Legend (2)}

There was something captivating about simple, repetitive tasks, especially those where the worker can see clear progress.

Although it's complicated to say, activities such as embroidery and weaving are hobbies that have been practiced for over four thousand years in both the East and the West.

In Qing's hometown, the hobby of looking at and manipulating screens was also said to be part of it.

Especially, the sense of accomplishment when it's completed was indescribable.

That was exactly how Tian Yuxue felt as he studied the map of Zhongyuan.

It was like that until the verdict came down that I had suffered and was useless as if I had been squeezed out as soon as I finished.

"What……?"

"Essence Absorption Demonic Art, Xi Xing Dafa? Ah. You don't know about the Killer Among Killer Technique. It's the worst Demonic Art, so horrific that it's not even considered one of the top ten Demonic Art, but a separate category, so terrifying that it's considered the worst."

It felt awful being called ignorant by the most ignorant person.

If you listened carefully, you would eventually realize that she didn't really know what the Essence Absorption Demonic Arts was.

Just like in the hometown of Qing, 'Today we'll learn about the Essence Absorption Demonic Arts. It's truly amazing. You should be careful, right?'. It's like a post full of pictures with no added information.

So, it's a great disgrace that must be passed down as a family motto from generation to generation, telling people not to forget this grudge while gnashing their teeth.

But Tian Yuxue was too distraught for that.

"What are you talking about? I worked so hard to get the map right, and I spent two months cutting back on sleep, and after the lecture, I'd stay cooped up in this gloomy basement room until bedtime…"

"Hmm. Couldn't that map and this map be different?"

"Give me that!"

Almost like a teleportation, Tian Yuxue leapt forward in front of Qing in one step, hastily took out her map and spread them out.

"This, fuck."

A spark flashed from Tian Yuxue's eyes.

"No, if there had been such a detailed map, why didn't you bring it in first…!"

Tian Yuxue glared at Qing fiercely, but soon sighed at her innocent expression.

"No. What's your fault? This is it. Look, it's the same map. This one's drawn in much more detail."

"Same map?"

"The detailed version is the original. Someone must have copied it from this. They even used a code to prevent being caught. Perhaps it was copied secretly and circulated, and then it ended up in the hands of Lulin guys. Haha. Two months. Hahaha…"

Tian Yuxue staggered over and sat down on a chair with his chin rested on his chest, as if he had no energy left.

Then suddenly he screamed.

"It's too noisy! Make those bastards stop whining!"

"Don't you have any questions? Should I just kill them or bring them to the authorities?"

"Please spare us…"

"Haiyaa. Why did you bring them up in the first place?"

"I thought you might be curious about something."

"Find out where he got the treasure map."

"They said they found it in an anonymous grave near the border?"

"Ha. What else is there to ask? Let's just put it aside. Right, it's the Essence Absorption Demonic Art."

Tian Yuxue smacked his lips.

"If only I could find the treasure and find the Secret Manual. Haiya. I'm completely drained. I can't just leave that horrific existence alone…"

"Is the Essence Absorption really that dangerous?"

"Of course it's dangerous. What kind of question is that?"

A representative method of stealing someone's energy was the sex tricks of the traditional Daoist.

But would someone else's true energy come and seep in just because they tell you to?

So, the Dual Cultivation of Daoism, which was the nurturing of mutual growth, was not to take away, but to share with each other. It was not an act of absorption, but a gift, so strictly speaking, it's not an act of theft.

Of course, original method was still of swindling, and it's usually the pereferred method of seductress practitioner.

Since it cannot be taken away just like that, they lead people to become confused and lose their souls, and only after driving them to the extreme with overwhelming pleasure can they take away the victim's energy.

"Wait, why the sex story so suddenly?"

"Look. It's that hard to steal someone's True Innate Qi. But Essence Absorption bypass all that. They say it just sucks it out the moment it touches you."

Just touching it sucks out the True Innate Qi, so it's not just a matter of losing Qi.

Just by touching, the flow of Qi and blood was forced outward.

That is, it means complete suppression of Qi and blood.

Just by touching the body, the internal Qi was neutralized and at the same time, the True Innate Qi was extracted.

It doesn't even consider the level of Realm.

Even if they were just a rookie who had just learned the Essence Absorption, if he could somehow hold on to the master of Unrestrained Realm, they could neutralize their powerful Innate Qi.

Of course, if you are a master of Unrestrained Realm, you are a superhuman with strong external skills.

If a youngster who just learned the Essence Absorption rushes straight to Unrestrained Realm, they'd just be beaten up and die like idiots.

And the new owner of the Essence Absorption will further increase their own level with the internal energy they had taken and swallowed.

"Huh. Isn't that too much of a scam? Why does such a martial art even exist? It's ridiculous. And it doesn't have any weaknesses, right? If you get caught, it's over."

"They say you're vulnerable while absorbing, so don't fight it alone. Isn't that why they call it the most lethal, most dangerous Demonic Art? They say the side effects of absorbing it can even drive people mad, so someone who can harm others with just a touch is truly a madman."

"Why'd they go crazy?"

"'A person's True Qi is essentially their soul. How can someone with multiple souls maintain their sanity?' they say. But I've never held another's True Qi, so I'm not sure about that. Or perhaps it's because that martial art are so powerful that they treat them as something evil and seek to erase them."

"Hmm."

"But since none of the masters of the Essence Absorption were sane, it seems the rumor that they go mad isn't wrong. Or because they possess so much power, perhaps they simply see another humans as pockets of Qi to be sucked? Perhaps they no longer see people as people."

And then Tian Yuxue stood up.

"So shouldn't we get rid of that vile thing?"

"Huh? Us? Why?"

Tian Yuxue suddenly losts his temper.

"You bitch, are you calling yourself the next Divine Thief? Isn't it the Divine Thief's job to clear out the world of harmful treasures?"

"Ah. That's right. I'm the great Divine Thief."

"Not yet. Is this okay? I wonder if I've caused great trouble to my ancestors."

The Hanlin Academy's Scholar of Literature was the Divine Thief!

The Heavenly Blossom Sword was the next generation's Divine Thief candidate!

The Three Fiends of Bingzhou desperately pretended not to hear this surprising fact.

They wanted to live.

Of course, that only stopped at 'trying' stage.

If they really wanted to live, they shouldn't have lived like that.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Chen Changming's eyes sparkled when she heard that they were leaving for Shandong.

"Are we going to see the sea?"

"Oh, is that a neighborhood with an ocean view?"

\textit{I don't know the geography of Zhongyuan, so I know that Shandong Province was adjacent to the sea, but I don't know if that area was on the coast.}

\textit{Come to think of it, Chen Changming was from the seaside.}

\textit{Although she wasn't born by the sea, I heard that she spent her childhood in a coastal city.}

"I wish I could see the ocean. I'd like to eat grilled clams."

Chen Changming spoke in a rare Qing-like voice.

Qing's palate was more about meat than seafood, so seafood was good to eat, but if it's not available, then just don't eat it.

But Chen Changming, even if she didn't say anything, probably kept thinking about the seafood that she couldn't eat inland.

For example, something like those grilled clams.

Because it's a delicacy that can only be found in the seaside, it cannot be eaten inland due to the undeveloped logistics situation in Zhongyuan.

\textit{Now that I think about it, I guess I was a bit inconsiderate.}

\textit{No wonder she liked those shell earrings.}

It wouldn't be such a dangerous journey, in Qing's opinion.

Just go, look at the map, wander around a bit, maybe dig some land, or maybe wander around some ancient ruins like Mr. Jones.\footnote{Indiana Jones}

Then, when you find the Secret Manual, burn it and come back, and you're done.

"Yeah. We can just go to the beach or somewhere near the beach. Let's go and eat all the grilled clams we want. Hmm. I wonder if there's a place in Zhongyuan that offers all-you-can-eat clams?"

Well, Qing's pouch were filled to the brim with golds and silvers.

Even if it's not a pouch with endless capacity, it's still a pouch thick stack of promissory notes that's enough to have endless fun.

So on the last day of July.

For reference, the waning crescent of the lunar month was called the last day of the month, which meant that they left Taiyuan as soon as the Great Study Hall vacation began.

This must be truly regrettable news for the scholars of the Hanlin Academy who were trying to knock on the doors of the Scholar of Study's mansion, with a pure desire to learn during their vacation.

\textit{Anyway, I'll rent a carriage and-}

There was some opposition from Tian Yuxue to renting a carriage.

"Why bother renting a carriage when you have a good feet?"

"But it's hot."

"Isn't it even more hot riding in a carriage? Haven't you ever ridden in a summer carriage? You'll get steamed because you're surrounded on all sides. It's also stuffy."

"It won't be hot if you ride with me."

"…?"

Here goes the human air conditioner itself, Ximen Qing!

It was a cool, chilling aura emitted by the overwhelming output of immense Inner Qi that has transcended the realm.

The small interior of the carriage quickly cooled down to a comfortable temperature.

"Ah, this is nice. I'm enjoying all this luxury thanks to my good disciple. What kind of luxury is this in the middle of summer?"

"See? It's nice, isn't it? But is Changming cold? You seems a little shivering."

"I'm n-n-not c-cold."

Chen Changming, who was snuggled tightly in the arms of Qing, was blowing out a cold wind, buried her head in the soft headrest with an expression of bliss at first.

But if she had to say, she was sitting right in front of the air conditioner, so she got goosebumps and her body was shivering.

It seems like she would rather wear more clothes in midsummer than get off Qing's lap.

From Taiyuan, they go south to Henan.

She was thinking of looking around in Zhengzhou, but no one seemed to want to get out of the carriage.

Since only Qing could feel cool outside, in the end, they decided to hurry up and go using the democratic process of majority rule.

Arriving at the familiar Kaifeng, what on earth was this?

"Wow. They're practically walking around naked."

Zhen Sui said that low-cut would be very popular this summer, and she really wasn't joking. They're going around wearing only the middle part.

They covered it with a see-through cotton cloth, as if they didn't want their chest to burn, but, well, it was a truly pleasant sight to see.

Qing's gaze couldn't leave the passing woman, so Chen Changming followed her gaze, looked down at her own, and felt very depressed.

\textit{Shit, they keep showing off their chests, so I can't help but notice it, and my hands are getting restless.}

\textit{There's a little one in my arms, but it's a bit awkward in front of Master.}

\textit{But what about this density of the woman?}

Qing soon noticed something familiar about this sight, but now was not the time to expand the group.

If they were just out for fun, it might be okay, but since they're on Divine Thief business, it's a bit much to go looking for the Jade Kirin since it's highly likely to appear.

So, after Kaifeng, they go straight east.

When theye arrived in Shandong Province, the sun was shining brightly and the heat was even more intense.

Passing through the land of Jinan, Zhangqiu, Zibo, Qingzhou, Weifang, and Laixi.

If you turn south from Laixi, you'd arrive at the destination, Jimo.

And there was a huge mountain located to the south of Jimo so you could see the entire mountain range from Jimo without having to go far.

"Master, surely it's on that mountain."

"Yes. It's on that mountain."

Qing face has turned completely pale.

It was not as tall or majestic as other mountains in Zhongyuan.

But isn't it really wide from left to right? By just looking at it, you could tell that the mountain range wasn't just any mountain range.

"Is there, by any chance, the exact location?"

"That's what treasure hunting is all about. You keep searching until you find it."

That meant he didn't know.

Qing sighed deeply.

Then suddenly she had a strange feeling.

\textit{Why do people sigh deeply when they look towards Mount Lao?}

\textit{Why? Is there a custom of sighing while looking at the old mountain?}
