\chapter{Every Treasure Has a Sad Legend (9)}

Still, Sotalmyeongdo Osanchu was quite at ease.

This was what Osanchu thought.

If you were going to kill me, you should have killed me a long time ago.

Why would you roll up your arms and legs in a blanket after breaking them?

He said that he would either hand it over to the authorities or, since he was afraid of the repercussions of his father, who was a master of the current situation, he would wrap it up so that it would not get hurt any further.

I think the atmosphere there was pretty good.

Fearing that his own resentment would also affect his son, Talmyeongdo Oh Daean passed on his survival technique to his son.

If you are captured by the enemy, keep talking to them somehow.

If you don't know someone, you kill them without a second thought, but if you know their face and name, you will inevitably be shocked.

And pretend to be friendly.

Don't show resentment, talk to your worst friend.

It was human nature to be more generous to those I know, so it's never easy to harm someone I have spoken to.

Of course, I told you not to show your resentment, I didn't tell you to give up your resentment.

So, Osanchu was just swallowing his resentment inside.

Fucking bitch. We'll see.

Even if I have to wander for the rest of my life, I will definitely avenge this disgrace.

I'll catch all your family, relatives, and friends, and put them in your mouth one by one right in front of your eyes.

This could be said to be the way an apostle takes revenge.

Anyway, I can't talk any more since I'm gagged, so I'm just imagining the moment of revenge that will come in the distant future.

How will you cry, four years later? Instead of killing you, I will cut off your limbs and keep you alive for a long time, making you regret being born in shame and pain.

The thought of revenge was sweet.

At least that was the case until Qing, without any hesitation, thrust a torch into the third brother's blanket.

"Ugh!"

The blanket was fluffy.

If you are wrapped around someone with broken limbs, no matter how much you wiggle inside, the only thing you can do was wiggle.

And also, the blanket burns very well.

The flames spread in an instant, engulfing the human larva and human blanket in an instant.

"Eww! Eww!" "Eww!" "Eww! Eww!"

Why!? Wasn't it supposed to save me?

Crazy bitch! How dare you wear human skin and burn a person alive!

Urgent voices of this kind are muffled and escape through the gag.

"Okay, let's go!"

Qing kicks his third brother who was burning.

Of course, the third one, with legs that are three times stronger than arms, leaps up and attacks his sworn brothers.

The Osanchu at the very end desperately rolls its body away.

But soon the chin.

As if the soft blanket were lifting my body, the world suddenly turned around and I was suddenly drawn closer to my brothers who were on fire.

Six burning human horses.

Qing watched the scene quietly.

Suddenly, the sound of a fire dying.

One of the guys rolling around ended up in a pool of blood flowing from the pile of corpses of the villagers.

Then, they all have anxious expressions and roll towards the pile of corpses.

Even though he was covered in a blanket, if his already broken limbs were crushed, he would be in great pain, but he was still determined to survive.

I tried to live like that, but ended up entangled in a pile of corpses that I had massacred.

Qing watched for a moment, wondering if someone would come out to put out the fire, but how much blood could have pooled on the dirt floor?

When suffering from full body burns, patients are said to lie face down on their knees and arms on the bed.

Because it's so painful for the affected area to touch anything, it's said that the position was taken to minimize the area of ​​contact as much as possible.

Wouldn't this be an appropriate punishment for those who massacred villagers just to learn the geography of the mountains?

But, should I have let go of the gag?

I wrapped him in a blanket, and he just rolled around even though he was freaking out, and he couldn't even scream, so I'm really upset.

Ah. I want to hear a scream.

But if it's too noisy, Master might come out. Jang Myung might come out.

It's not a scene for the elderly (or not) or children (or not) to see.

Qing watches the human blanket that's burning brightly with a satisfied expression.

In your hometown, do you call it a bulmong?

As I look at the fire, my mind becomes at ease and my worries seem trivial.

Yes, I am not some kind of heavenly agent, an apostle of justice, or a judge of evil deeds, and I am not going to kill all the wicked people in the world.

All I have to do was burn each and every dirty thing I see and every evil person I touch.

Then, suddenly, a loud, thunderous sound like a bolt from the blue echoed from his stomach, and Qing's expression became blank.

His eyes were squinted, his eyebrows were arched, and his mouth was gaping open, saying, 'Ah. I'm hungry.'

If someone were to see it, they might feel a strange urge to observe it from a distance.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The man's sword cuts through space.

Each and every sharp sword strike was heavy and powerful, and it's a powerful heavy sword with a wedge-like force.

Then suddenly the man's left hand reaches out.

It was an excellent technique to fill in the gaps in the sword, but the man just stood there with his hand outstretched, his eyebrows trembling, and his expression pained.

I have clearly decided to achieve greatness with my sword!

How can you pursue a small profit right in front of you and use something dishonest and cowardly instead of a sword?

By the way, the man's outstretched arm was my left arm.

Namgung Shinjae, the man who had instantly turned his left arm into a cowardly being, was in agony.

A true swordsman speaks only with his sword!

But, was it really necessary to push forward something that everyone in the world says was not true?

Or was it because I am not a genius, because I am not a swordsman, that I cannot reveal these truths to the world?

Suddenly, the illusion of the black rain comes to mind.

While eating rice with a knife, Geomwoo points at him thoughtlessly as usual.

Geomwoo's voice was played back as an auditory hallucination.

-What's the climax? It's embarrassing, so why don't you go out and swing your sword? Looking at the climax of the sword was ruining my appetite.

"Ugh."

It's annoying! It's so annoying that I want to squeeze it!

But wouldn't that be a distant dream for Namgung Shinjae?

The welcome and hallucinations continue.

The translucent black rain speaks with a dagger in hand with an expression of extreme meanness.

-Namgung Shinjae, you are more suited to be a swordsman than a swordsman.

Then, with a mean and nasty expression, he sticks out his tongue and licks the dagger blade, then spurts out blood while saying, "Ah, ah …

"Hmm. Looks good."

Namgung Shinjae nods his head, saying it's good.

If others had seen it, they would have gone on to say that the eldest son of the Namgung family was possessed by a demon and was now seeing and hearing things and muttering to himself.

I would say it's fortunate that the closed training was in progress.

Then, suddenly, huh?

Namgung Shinjae's eyes widen.

Come to think of it, wasn't that swordsman who practiced the strange practice of using a sword instead of a hand?

A sword instead of a hand. A sword instead of a hand?

Then suddenly a bolt of lightning strikes.

Yes!

If you only pursue swordsmanship, why don't you just hold a sword in your left hand and use swordsmanship?

This was it! It's a double-edged sword, a double-edged sword!

Twin swords are two swords that are handled as one and combined into one martial art, so it's called twin swords technique.

But what if you hold a sword on each side and use different swordsmanship techniques?

Swordsmanship was absolutely right and good.

And what if we add good to good?

Very good!

Why didn't I realize such a simple truth sooner!

I swore to become a true swordsman, different from others, by following only one path: the sword, but I, too, ended up being bound by the world's perception.

The reason why you don't usually hold two weapons was because they inevitably become entangled.

Usually, the left hand (or right hand depending on the person) was empty and the weapon was assisted with the recommendation, the ground method, and the gold and silver method.

Martial arts such as dual swordsmanship, dual sword technique, or left-handed swordsmanship were originally created with the premise of holding two weapons.

However, if it's not a dual-wielding martial art, holding the same weapon in each hand and using different types of martial arts in each hand was considered extremely foolish in the martial arts world.

Because martial arts was the manifestation of the mind.

You can't swing a quick sword with your right hand and a magic sword with your left.

Because the human mind cannot keep up.

It will be easier to understand if you draw a square with your right hand and a triangle with your left hand.

But someone can!

It's not that it doesn't exist, it's that it's difficult.

If there was even one person who can do it, it's not impossible, it's just difficult.

Namgung Shinjae stretches out his trembling left hand.

Finally, an ebony wooden sword that can be held in the left hand.

It's as if he's acting cute by wrapping his arms around her as if to ask why she's only holding onto him now.

In that moment, all of Namgung Shinjae's accumulated sword experience exploded at once.

It was the true embodiment of the swordsmanship that I had known in my head and practiced in my body.

Climax review!

The black sword of the Namgung family's king.

But was Namgung's sword the only one?

There was also a free sword that stretched out endlessly and played in the endless sky.

The sky was clear.

Yes, that's right.

To begin with, Namgung's sword wasn't one, so the reason Namgung had two arms was to hold the Emperor and the Changgung in different hands!

Suddenly, a huge wall appears before Namgung Shinjae's eyes.

However, Namgung Shinjae's body was already floating up.

Into that vast sky.

However, there was a hand, or rather a sword, that grabbed the ankle of Namgung Shinjae who was flying high like that.

-You shouldn't come up lightly.

An emperor was one who maintains his position, one who stands tall like Mount Tai and blocks the sky, one who looks up to the sky.

A heavy presence that must always keep its place.

How can you so lightly fly into the sky!

Namgung Shinjae lamented.

How can the swordsmanship of one family have such different, diametrically opposed images?

According to the elders of the direct lineage, only by enjoying and feeling freedom through the Changgungmuae Sword can one fully feel the weight of the emperor at the moment of proclaiming oneself as emperor when the time comes and one reaches the realm.

But Namgung Shinjae's expression was firm.

No, Changgungmuae was also my precious sword type.

Then I will become a free emperor!

-That's impossible!

"Who dares to say impossible!"

-You will walk a more difficult path than anyone else!

"Difficulty was already life to me! If I had chosen the easy way, I would have broken my vow to live as a swordsman long ago!"

Namgung Shinjae shakes his foot.

And it flies up.

The sky was boundless in all directions, without any obstructions.

Suddenly, Namgung Shinjae realized that he had flown past the wall.

It's a very messy realization, though.

Originally, the enlightenment of the unmanned was very personal.

The wooden swords in the right and left hands are adorned with light blue and sky blue starlight, respectively.

This was Kang-gi. Is this the ultimate power?

Namgung Shinjae opens the door to the training ground.

Now was the time to declare to the world that the successor of the Namgung family had reached the pinnacle of power.

Why was the only one welcoming the general?

"Congratulations, Grand Duke. However, the Lord and Lady have departed for the land of Sacheon."

"Hmm? What's going on?"

"They just said they were going out to have fun. They left all the work to me. That's really too much."

"Hmm. If I'm not careful, I might end up with a younger sibling who's like my own child. By the way, the Changgungdan training grounds are empty. Is something wrong?"

"There was a strange rumor that a new god had appeared in Shandong, so I set off for there."

"Shingabibo? Isn't it the only treasure that can be called a family treasure bearing the Shin surname?"

"That's why the Archery Corps came forward. We can't just sit back and wait for the results to be known, whether it's real or fake."

"Hmm. Right."

Namgung Shinjae touches his chin.

The parents who would have reported the achievements are absent, and the warriors of the Changgungdan who would have invited them for a sparring match are also absent.

Well then I guess I'll just have to do some more closed-door training.

That was when.

The general looks at Namgung Shinjae and smiles sinisterly.

"Ah. Now that the Lord of Soga has achieved greatness, it's time for you to take on the duties of the Lord of Soga in earnest."

"Huh? Suddenly?"

"The Lord of the House has stopped you, saying it's time to reach your peak. Now that you've reached that level, shouldn't you begin preparing in earnest to lead the clan?"

"Hmm. Hmm."

Namgung Shinjae nodded with a serious expression and thought.

At this rate, I'll end up doing all the work in place of my father, who's out training and playing.

Hmm. I guess I'll have to run away from home first and think about it.