\chapter{Every Treasure Has a Sad Legend (4)}

First of all, I had to secretly watch out for the things I was doing in Mount Lao, because the Divine Thief's intention was always to steal.

If you plan to kill everyone and take everything away, was that considered a new fight?

The problem is, it's the next generation of Divine Thief that really seems to do that.

So, as a teacher, you must teach the correct way to practice Divine Thief, at least that's what Tian Yuxue thought.

First, like a wasted tourist, I start eating and drinking from the morning, blaming the bad weather for nothing.

Then, I thought, "This won't work, let's go," and left the silent zone for now.

And in a remote, uninhabited place, Tian Yuxue changes into shabby clothes that he has stolen from somewhere.

To be exact, it's a shabby outfit that was purchased without the consent of the hermit.

Because it's the law that a thief should not prey on the property of innocent civilians.

"Excuse me, Master? Aren't these men's clothes? They're so loose that if I jump, my chest will pop out."

"Pretend it's pretend. Why did you bring men's clothes? And what's sticking out? It's sticking out. There's nothing a woman can't do. Wrap it tightly and hide it."

"It's stuffy and uncomfortable. If you keep being close to each other in this weather, you'll sweat. It's different from the sweat you shed because it's hot. It's sticky and gritty. Ugh, what's the name?"

"Do I have to hear that explanation?"

"Miss, this was really disgusting, and I don't know how to explain it. Yeah, Jangmyeong, how I feel… I don't know."

The tendon on Chen Changming's forehead snapped.

"I would have known even if I hadn't been sick."

It was Chen Changming who blamed the delay of the sound of the sky.

"Uh, um. No. Yeah. Yeah. If that's what you're saying, then that's what it's."

Could it just be a genetic problem?

Suddenly, Changming'er's mother, Yang So-wol, came to mind.

But I didn't think it was necessary to bring up that woman's story, so I just mumbled and said, "Okay, I see."

I even put a rain cover on it to avoid the rain. Hmm. The rain cover was also used.

"Ugh, it smells. Can't you just buy a new one and use that?"

"that's right."

Chen Changming nods his head vigorously.

But Tian Yuxue just laughs.

"You're dressed shabbily, but your hat was brand new and shiny? Is that okay?"

"Hmm. Do I really have to go this far?"

"It's said that wealth can be lost, but life should not be coveted. Huh? Don't you understand what I mean?"

"Hmm."

Qing's expression became ambiguous.

I don't really agree with it, but it's about keeping dangerous things away from dangerous people.

Then why don't we just get rid of the dangerous ones?

But I can't just tell the Master to kill them all, so I just have an ambiguous expression.

Divine Thief sighs at the sight.

Anyway, with those old clothes and shabby hats on, it looked like three generations of beggars, one old and one young, were standing side by side.

"I'm not a beggar, I'm a herbalist. Do you think I'm wearing a hat for nothing?"

In fact, to others, a herbalist wearing a rag, a sack, and holding a stick looks like a proper herbalist.

It was common to see herbalists passing down their herbal medicines by word of mouth, with old people, young people, and children wandering around in groups.

After finishing my makeup in that deserted wilderness, I quietly head towards the pathless terrain of the old mountain.

In fact, this was how the common people in the rural areas of Zhongyuan are.

He looks like a beggar, but if he holds a plow, he's a farmer.

He looks like a beggar, but he wears a hat and becomes a herbalist.

He looks like a beggar, but when he holds a net, he looks like a fisherman.

In the first place, civilians' work clothes were worn roughly, and when they became unusable even as rags, they were thrown away and new ones were made.

I wondered if it really had to be this way.

"Who are you!"

As soon as I climbed a little up the ridge of the mountain where there was no path, I thought a small mountain path would appear, but as if I was sure of it, a man who had been loitering on the side of the road suddenly shouted and aimed his sword.

"Oh my, Nari. Why, why are you doing this?"

Tian Yuxue's acting was plausible.

Since Qing wasn't particularly confident in acting, he just pretended to hug Chen Changming and cover his back.

It's like imitating a father who takes care of his children.

The unmanned man lowers the tip of his sword.

"What, are you hunters?"

"Yes, yes, that's right."

"Hmm. Oh, right, that's a good thing. Do you visit Mount Lao often? Is there a large cemetery or mausoleum there?"

"Oh my, Nari. Who would build a grave on a mountain, especially a rocky mountain?"

"Really? Then, what about the suspicious cave?"

"If it's a blood type that avoids rain, there are things that have been used for a long time, but you say it's suspicious…?"

"Huh. Those things aren't much help. It was just bad luck, so don't blame me too much."

And then he suddenly swung his sword -

Tian Yuxue's arm naturally extends out, and his hand touches mine as if shaking hands, and he naturally receives the sword as if he had planned it.

Pickpocketing, the art of extreme sleight of hand.

"Huh?"

The unmanned vehicle, which had been waving its bare hands in the air from the middle of the game, made a stupid sound.

"Tsk. What good was it to swing something so ugly around so carelessly? You really are a bad guy."

Tian Yuxue stabs the warrior's neck with the sword he took.

I thought there would be bloodshed, didn't I?

Even though I stabbed him with a knife, he just grabbed his neck and coughed dryly.

Tian Yuxue turns around and wraps his arm around the man's collar, holding him tightly.

The man was struggling, but Tian Yuxue only swayed strangely from side to side, his strong arms remaining in place, blocking his breathing.

Eventually, the man begins to slump.

Anyway, Qing knows that Tian Yuxue was a master of Hwa-gyeong.

I've never seen a fighting style like Tian Yuxue's, somewhere between soft and liquid, but, well, it's great, but not my style.

However, I had no idea what Chen Changming was.

The old man I thought was a highly respected scholar turned out to be a master!

Chen Changming pokes Qing's side with his eyes forming perfect circles.

"Huh? Why?"

"You're an expert. Did you know that?"

"Hmph. Jang Myeong-ah. In the martial arts world, you have to be careful of the elderly, women, and children. Just look at us: the elderly, the women, and oh…"

Qing looked at Chen Changming and said, "Hmm."

"Come to think of it, I guess I don't need to be careful with the child. Just let your guard down with the child. Little one."

"……?"

While Chen Changming tilts his head wondering what it means, Qing accepts the man from Tian Yuxue.

He naturally wrapped his hand around the man's hair and held on tightly, then followed Tian Yuxue and dove into the trees across the street.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tian Yuxue's class on the art of entrapment.

"If you tie it like this, even if it's tied with vines, it's so strong that even a general cannot untie it."

Qing thought it was nonsense, and didn't feel the need to hold back on what he wanted to say.

"Hey, strong power destroys everything, right? The bonds won't break? A stronger power!"

"Hmph. No matter how strong a person is, there's always a point where their power exerts its influence. If you overpower that point, you can't move."

"Then wouldn't it be that I don't have enough strength?"

"Then, shall we tie it up once?"

"Let's give it a try, okay?"

And then, oh my, hot! Thud thud!

Qing shocked Tian Yuxue by bursting the bonds with pure force.

"No, what kind of power was this, so ignorant, no, what, what was this, huh, really. Haven't you ever heard of a female protagonist?"

"No, Master. You said you couldn't solve the Hangwoo Jangsa. I don't want to be compared to someone weaker than me."

The Hangwoo merchant can't solve it, but the Qing can?

It was a clear reason why the Qing should be called the Southern Heavenly Flower, not the Xiang Yu General.

Whether so or not, Tian Yuxue was truly impressed.

Somehow, the oil tank training center was becoming increasingly useless.

Is this really the power of humanity?

Although I don't know the exact physical mechanism, such as the force point, the point of application, and the principle of the lever, it's a binding technique that binds the muscles and bones in a way that makes it the least amount of strength a person can exert.

Doesn't that mean that even with the weakest strength, it can cut down something like a tree vine?

"Let me go. This won't do."

Chen Changming, who had been writhing on the floor while using his dragon, declared his surrender.

I saw the Ximen Qing's new spirit and said I would try it too, but I ended up looking like a magpie with a torn leg.

Qing's eyes narrowed.

Oh, that's strange.

Why do I want to tease, tease, and bully just the little things?

But there's nothing wrong with that, right?

There's no need to endure it, right?

"Changming'er. Attempting something you can't handle was called recklessness, and the irresponsible attitude of thinking someone will help you if it doesn't work out was called positive distortion. How can you possibly survive in the harsh world of martial arts like that?"

"……?"

"It breaks my heart, but I will teach Jangmyeong a great lesson."

So, Qing grabs Chen Changming and starts tickling him.

Kyahahaha, the young girl's characteristic ultrasonic laughter bursts out, and then soon, kaauk, kaak, stop, kyaha, it seems like she's starting to lose strength little by little.

Chen Changming initially laughs it off as a joke, but then he starts to feel short of breath and his stomach starts to hurt so much that it feels like it's going to tear apart.

Stop, me, breath, kyahahaha, the sound gradually changes to a gasping for breath.

The man comes to his senses in that chill.

"Ugh. Ugh! Ugh!"

I couldn't hear what he was saying because his mouth was blocked, but I could clearly feel his determination to come to his senses.

Thanks to this, Chen Changming, who was freed from the tickling torture of the Ximen Qing, collapsed on the floor, gasping for breath.

"Okay. Now I understand. Don't trust people so easily."

"This was too much. Whoa, I almost died."

"No matter how much you tickle someone, it won't kill them. They won't feel anything even after halfway through. Would I do something dangerous to my Jangmyeong?"

I don't know if it's because they block out their senses to survive, or because they quickly become numb to external stimuli, but no matter how much they tickle, they adapt before they can breathe.

I've tried it on villains before, but they were so funny they couldn't kill them.

"Okay. Come here."

"joy."

"You're not coming? I'll count to five. One, two, it should have been like this a long time ago."

It was Chen Changming who quickly entered Qing's arms.

Qing sits on the floor, hugs Choco, and exhales cold air to cool down the heat.

This was the so-called act of giving medicine after giving a disease.

But Chen Changming, who was always hungry for his older sister, completely forgets the hardship he had just suffered and his expression softens in the pleasant cold air.

The man who was caught was still crying.

But no one cares.

Tian Yuxue was so dumbfounded that he ends up asking.

"What are you doing?"

"Hmm. Are you going to take a look? Aren't you going to interrogate me?"

"Ugh, ugh!"

"No, what good was having a disciple for? Should an old man be left to do all the annoying work?"

"Eww!"

"Hmm. If I do it, it'll get a bit bloody. Children aren't allowed. Um, Jang Myeong-ah. Can you go pick some flowers?"

"Ugh! Ugh!"

"I'm twenty years old."

"Oh, my. You can't lie. How can you be twenty, kid? How old was your life? Twelve? Oh, where are you going?"

"Let go."

Although Chen Changming was struggling, it could also be said that he was wasting his energy for no reason.

"Is there a way to get someone to answer my questions without getting bloody?"

"Well, there was a technique called the ‘Bungeunchakgol'."

"Eww! Eww! Eww!"

"Bungeunchakgol? Oh. I like the name."

Tearing muscles and breaking bones?

Just hearing the name makes it sound so fun. But…

Why does it look familiar?

Isn't that the principle of oil liquefaction?

"Ah. Would you like to learn this now? It's a technique that forcibly reverses the flow of qi and blood, causing spasms in the muscles throughout the body."

Qing's eyes flashed.

Causing muscle cramps throughout the body?

Makes all your muscles cramp up?

Such a terrible method?

I want to learn right now!

"Oh. I want to learn! I want to learn! Please let me learn!"

"However, the opponent's internal energy must be completely subdued. Unless they're a master of point magic or know some kind of forbidden technique. If I'm going to show you now, I'll have to break this damn dantian."

"Ugh!"

Ah. Now that I think about it, I should have asked Hwiyoung to teach me the Golden Dharma.

When I kicked him and paralyzed his lower body, well, now that I think about it, I feel bad about it.

Anyway, thanks to that, since he was hit by some great law, he would continue to be a god of outbreaks, so the demonic cult guys were completely at ease and didn't suspect anything.

So, performance was guaranteed.

Well, I'll see you later, so just tell me then.

"That's right. If there's a way to cleanly break the danjeon, please let me know. Every time, my danjeon and internal organs burst and I die."

"Eeeeeep! Eep! Eep eep!"

The man shook his head desperately.

I realized that I had made a very wrong decision, and that I had ended up being captured by some very vicious bastards.

So, he keeps sending his eyes filled with earnest appeal to the old man, the young man, and the child.
