\chapter{Every Treasure Has a Sad Legend (6)}

Thanks to Qing's meticulous treatment, the legs will be able to move normally.

If you apply too much force, your knees will give out and you will fall over.

So how will he live now?

Will I be able to live like an ordinary person?

Or will I become a wreck, torn between hatred and an impossible revenge for the rest of my life?

Either way, it was truly rewarding.

Either you change your mind and live a healthy life, whether voluntarily or involuntarily, or you live a life of suffering, unable to shake off the pain until you die.

The former benefits the world, the latter pays the price for evil deeds.

But you could probably run to that big sect and report it.

Those bastards disguised as herbalists came in and did this to me, so I feel wronged, so I want revenge. Sob, sob, something like that.

Well then, wouldn't you be a little angry?

Hmm. I guess I should have killed him.

But there was a teacher and there was also Jangmyeong.

Hey, let's not dwell on the past.

"Hmm. So, what do you do now?"

"Oh my. Are you so peaceful?"

"What good does it do to be impatient? It's just a curse and a curse on the mind, you know?"

The saying "The desire to overcome adversity" was from Confucius, and the saying "The wisdom to overcome adversity" was from Mencius.

Both of them mean that if you rush, you ruin things, which was the same meaning as the proverb from Qing's hometown, which says that the more you rush, the more you have to go back.

At that, Tian Yuxue snorted.

"Hmph. You've barely skimmed through the Hundred Schools of Thought before you start writing. Well, that's about the time when I'm anxious to tell the world I've learned the alphabet."

Originally, it was the case that those who had only skimmed the surface of their studies would make a fuss.

In Qing's hometown, he was the pinnacle of ignorance, a person who has only mastered the basics and was full of confidence, pretending to know everything.

But isn't it like a chick squeaking out four Chinese characters and calling them idioms in front of a giant of Confucianism, a phoenix, or, if I may say so, a phoenix-like scholar?

So what are the phoenix's feelings?

Very cute!

Oh my, the chick can even write!

Are you a genius? Aren't you going to graduate school?

Instead of being a Bachelor of Science, I should try being a Doctor of Science.

Tian Yuxue couldn't hide his pleased smile.

"Yeah. But you're right. If we rush, the treasure won't escape. Well, we don't have time to relax, though."

"So, what should I do first? I can't just wander around the ground, picking up fallen leaves to see if anything's missing."

"Shinshishinmyohyangji. Didn't you say that Shinshi was where Shinmyo points? I think we should start by looking for a tall, raised feature shaped like a tombstone, tower, or something similar."

Usually, when we say "pointing" in these maps, we mean the direction that the shadow was pointing.

If it's a new city, the shadow will be facing roughly southeast, and if there's a formation or mechanism, the entrance may or may not appear only when the shadow falls at that time.

"Then, wherever the tomb is, we can assume it's somewhere sunny and high up. So, somewhere on the northern ridge. Let's start by looking for that sacred tomb."

"Oh."

It was a lot of information in just six letters.

After listening, it feels like a real treasure hunt? Some kind of adventure? Why, it taps into that instinct that makes people's hearts flutter.

Even if it's a trivial event in the land of Qing, if you say treasure hunt, doesn't it make you feel like, 'I've found all the treasures, I'll find them all'?

So, Qingdo was excited.

I think it might be fun somehow?

… … I thought, but, um, it's really wide.

Come to think of it, isn't this an event where prizes are densely piled up in a small space?

The mountain was wide.

There are trees blocking the view from below, and even if there weren't trees, the angle makes it hard to see what's rising above.

Of course, the high peaks are all rocky and treeless, making them open and clear, but that means the person standing on top can see them well.

Why would you sneak in and climb up a bare rocky mountain that's so visible?

So at first, I craned my neck to see what was rising above the ridge, but it was Qing who had eyes that were burning with his superhuman eyesight.

"Oh, Changming'er. See this? It's called Moktong. According to the Yellow Emperor's Classic of Internal Medicine, it cures all wind ailments and even restores a woman's health. It's a particularly good tonic for women. It's so gentle that they even recommend it for pregnant women to drink."

Qing was a well-educated female doctor, albeit briefly.

Even if you don't know the expensive ones, you can recognize the medicinal herbs that are commonly found in the public.

"What was it? It looks strange."

"Is this a flower? This thing inside, like a pod, was a fruit. It tastes… wow. Want to try it?"

"Yeah. Yeah."

He takes out a fruit that looks like a caterpillar's cocoon from between the strangely opened petals.

"Okay, ah."

"Uh. Hmm? Ouch, huh, eek……"

Chen Changming, who had bitten the meat without fear, kept spitting out saliva with a red face.

Qing giggles again, saying she's excited about that sight.

Chen Changming then banged his head on the table.

"Ugh, the bitter taste still lingers."

"Well, if it was tasty, I would eat it as fruit. Should I use it as medicine?"

"You just keep joking around."

"Okay. Rinse your mouth with this. Would you like some too, Master? It's not overly sweet, but it's edible."

All that was in my hand were small, wild berries, each one picked at a different time.

"No, I told you to pretend to be a herbalist, so why are you actually sitting there digging up herbs?"

"Hmm. I can see it…"

"If you look at the ground, you can see the herbs. I told you to look for the tombstone."

"But."

Qing trails off and turns her gaze towards the tall stone mountain.

In fact, when we talk about the stone mountains of Zhongyuan, we see that every peak that we see was sharp and jagged.

Everything I saw was like a tombstone, so I kept talking about it one by one, thinking, "Isn't that where it's?" and my lips started to swell.

In essence, information overload was a more effective method than information control.

People can easily find something interesting in a small amount of material, but when the list becomes endless, they end up losing interest in the whole thing.

"Then, did you really think that such a powerful magician would be lying in plain sight? If so, someone would have found it long ago and caused a bloody massacre. Would Jang Bo-do have survived until the whole world heard the news about the murder here?"

Qing cries out to him.

"What? Then, does that mean that the Absorbing Magical Skill was already gone before that and might not exist at all?"

"Ahem. This was it. This was all for the good of the world. Isn't this suffering all virtuous and ultimately beneficial to the world?"

However, Tian Yuxue's expression was not bright.

The road ahead was wide open, but when I actually came to Mount Lao, I realized that it was not as easy as I thought.

So, somewhere in the mountains, I came across some decent terrain. I had lunch, munching on rice balls, and wandered around the mountains all day.

As a result, the sky becomes dark, and the whole area becomes dark even though it's not yet time for the sun to set.

The dark, overcast clouds look like they're getting ready to pour down rain.

"Let's go back for today. We haven't even gotten very far yet, so why bother braving the wind and rain? Let's call it a day and go back."

The original plan was to spend the night in the mountains and look for a secret, but after looking at the first ridge, it was already getting dark.

So, let's really go deep into the mountains and do some searching and eating and sleeping.

It was time to go into the mountain and come out, and then start when the situation was not favorable to attract attention.

"First of all, let's ask the herbalists and mountaineers about the geography before we go. The terrain was more difficult than I thought."

"Hmm."

The expression on his face was subtle.

Tian Yuxue's expression suddenly turned sour.

"What? Why are you swollen?"

"No, you seemed like a very professional treasure hunter, but I guess you didn't have much of a plan."

"Hey, do you know how many times in life you'll encounter something like a market? You're definitely an expert at this. Why, then, do you keep searching, sleeping out in the rain?"

"Hehe. That's not it. Oh, raindrops. Let's go before it starts pouring down. Um. Jangmyeong, can you fit inside this bag? It's small, so I think you'll be able to fit just fine."

"why?"

"I'm going to hurry up and wash up and eat dinner. Since he's short, his legs are also short."

"My legs aren't short. Everyone said they're incredibly long compared to my torso."

"I'm talking about absolute length. Even if a long-legged magpie's legs are long, they're still short. Even if a stork's legs are short, they're still long."

The tendon on Chen Changming's forehead snapped.

Somehow, this was not the picture of travel that Chen Changming had imagined.

Instead of feeling affectionate like back then, he just teases me all day long.

Qing chuckles at that expression, then suddenly bends her knees and grabs her shoulder.

"Are you tired from wandering the mountains all day? Mountains secretly drain your stamina, don't you? Master and I are accustomed to overnight stays, but Jangmyeong isn't one of them. There's no need to overwork yourself."

"……huh."

A gentle voice that melts away any sadness.

It was completely foul.

It's unfair because you have to ignore it even though you know it.

"Okay. Want to go in first? Oh. What the heck, it really fits perfectly? Isn't it uncomfortable?"

"Yeah. It's surprisingly comfortable."

"I'm not sure if I'll be a little shaken. If you feel too shaken, let me know. Of course, that won't stop me."

"……?"

"Oh, raindrops! Master, hurry up. It's pouring down."

Tian Yuxue runs towards him, smiling brightly.

The speed of the active and reserve players was quite fierce as they run with determination.

In fact, even before the preliminary Divine Thief, Qing was already a master of running, having been acknowledged by Ximensurin as having achieved everything through lightness.

Since I didn't know the geography anyway, I just followed Tian Yuxue's back and ran, and at some point, my view outside the trees opened up.

The damp wind before the heavy rain makes waves crash against the still green rice paddies.

Running along the ridges of rice paddies that look like the night sea to my left and right feels refreshing, unlike late summer, and a smile comes to my face without me realizing it.

The sky was dark and cloudy, and smoke from cooking rises in the distance.

Looking at that sight, I can't help but swallow my saliva and suddenly feel hungry.

By the way, it's past dinner time, huh?

Miss. But it seems like a fortified village, um.

In places like that, they are very rude and wary of outsiders, so they don't open their doors to them easily.

Even if they open again, there are no restaurants, and the only home-cooked meals they serve are rice with pickled vegetables, vegetables sautéed in oil, and if you give them a silver coin, they'll kill a few chickens for you.

I guess it's a bit of a shame.

Before we knew it, the village entrance was right in front of us.

It was a fortress village, typical of remote villages, with buildings surrounding it like a wall and large gates between them.

As Qing was about to put down Jinjangmyeong, he heard deep, even breathing behind him, and ended up chuckling.

Tian Yuxue, who noticed him, steps forward and calls out to the person.

"Ahem, hey, you're not here?"

Then there was a rustle.

The person who was told to come out doesn't come out, and Chen Changming wakes up for no reason.

"What, you're awake?"

"Yeah. Are they all here already?"

"Not everyone's here. Now, look. Doesn't this scenery look familiar?"

The sensation of him pressing down on the back of the chair was transmitted.

Chen Changming, who had been standing back to back with his back to the other side of the net, turns around.

"ah."

A while ago, when Jangmyeong and those murderous bastards were chasing me while blowing their fucking whistles, I somehow managed to shake them off and came across a village like this.

At that time, I pretended to be a ghost and got a pretty good meal.

"Even though it was cold rice, it was really tasty. Right?"

"Yeah. I still think about it sometimes."

"Wow, how many years has it been since that was? Time really flies."

The vagabond who was always poor and ate dumplings and soup with no other ingredients has now become a rich man with an abundance of gold and silver.

Well, come to think of it, that was a long time ago.

Nothing was the same as it was back then.

Jangmyeong was taller than me.

It was a time when Qing was lost in memories for a moment.

"What, herbalists?"

A village gate? A castle gate? A defensive wall? A man's face suddenly appears above that structure, the name of which was truly ambiguous.

But what about the state of evil karma?

While Qing tilts his head, Tian Yuxue lets out a cunning voice like he was a peddler.

"As I was passing by, the sky was getting dark and the clouds were thick, so I stopped by to see if I could stay for the night."

"That bag looks heavy. Are you coming back from Mount Lao? Yeah, come in for a bit."

What? Isn't that a bit short?

Even though it's a remote place and unfriendly to outsiders, why are you being so rude from the first time we met?

The best way to instill manners was through nuclear fission, so why don't you just give it a shot now?

While Qing was internally struggling, the door opens wide with a creaking sound of wood twisting.

And the man's torso was revealed.

He was wearing dirty clothes with fresh blood splattered here and there, and he pointed his sword at me.

And then he said with a mean expression.

"I was already looking for a useful hunter, and you came to me on your own accord?"
