\chapter{Every Treasure Has a Sad Legend (7)}

Qing checks first just in case.

This part needs to be made clear.

"Hey, that's not pig blood, was it? If you point a knife at me in such a misleading way, I can almost understand why Yeo Baek-sa died."

There was an anecdote that when Cao Cao came to visit, Yeo Baek-sa sharpened his sword to entertain the honored guest, but when Cao Cao saw him, he thought, "This bastard was trying to kill me," and killed Yeo Baek-sa, his family, and all of his servants without a trace.

This anecdote shows Cao Cao's character, and this evil was the reason why the people of Zhongyuan despise him and call him Cao Cao Bandit.

In fact, the people of Zhongyuan spit on Jo Jeok as the worst villain, but strangely, the barbarians of the Far East revere Jo Jeok as a hero.

But why?

Cao Cao was born with the most silver spoon in his mouth in Zhongyuan, so he inherited wealth, connections, and an army, and he quickly gained power without any effort.

And he lived only for power, saying that he just wanted to be emperor without any cause.

Even though Cao Cao himself was a terrible villain who enjoyed the pleasures of massacring civilians, committing adultery, and betraying and sending his subjects to their deaths throughout his life.

So, a person should not live like Cao Cao.

So, it was only natural to double-check to make sure that Qing was not an innocent person.

But the man asks back instead.

"Do you see pig blood? Are the eyes for decoration?"

His eyebrows twitched.

There are definitely kids like this.

If you just ask and give a polite yes or no answer, there won't be any hurt feelings, right?

Why do you always respond like this?

Even if you are innocent, you will still receive two severe beatings from the teacher for manners and verbal correction.

It's a shame. So, I guess you have to fire two nuclear warheads.

"Could you please explain to me exactly whether it's human blood, and if so, why did you use human blood to create such an outrageous pattern on your clothes?"

The man hesitates a little at that.

Wouldn't it be natural for a commoner to tremble in fear at the sight of a sword, kneel down, and beg for his life?

But the two people standing there blankly showed no sign of fear, not even the little boy carrying the sack the older woman carried on his back.

Why?

If you are not a commoner, that may be the case.

Now that I look at it, the stick wrapped around the dead tree was not a stick, but a form of weapon that's secretly hidden.

The man slowly changes his attitude.

"I am a person who was also a shaman. Who are you?"

"Do you know about the blood type of Shisan?"

"The bloodsucker I know was a different guy?"

"It's not a blood transfusion, it's a blood transfusion."

"Huh. Even if their nicknames are like that, they're just imitators. At first glance, they're obviously first-class mid-level players. They're just that kind of kid."

The man was startled.

To accurately discern the realm even with a cursory glance, you must be at least a master of the Unrestrained Realm.

"Huh. First-class? Who gives a first-class person such a grand nickname as Sisanhyeoldo? No, who gives a first-class person such a grand nickname?"

Then, I heard a sound like annoyance behind me.

"That's just how Sapa people are. They make things up themselves and then spread rumors."

"Oh, so you're saying that the nickname you gave yourself was Sisanhyeoldo?"

Woogam broke out in a cold sweat.

"Those, the elders……"

The commonality between Sapha and Qing was that they are both weak and strong.

The manners officer who had left the house of Woogam, sensing something was wrong, hurriedly kicked the door and returned.

"Okay. So what's that blood? Even if you lie, it'll all come out if you wander around the town."

"That is……"

Woogam looked around, trailing off.

Then suddenly, he lets out a loud roar of "Brother!!!" and turns around and runs away.

"madam."

The judgment was not bad, but I did not catch the opponent who was running away well.

Exactly ten steps later, Woogam received a strong blow to his back and rolled roughly on the floor.

The power of Qing's cool Taekwondo side kick that he caught up to in three steps.

Qing, who landed nicely, raises his sword.

The Moonlight Sword (No. 10), a ignorant greatsword that has suddenly cleared away the surrounding giants and revealed its vicious size.

"No, why are you running away? I asked you, pig blood or human blood? Is that so hard to say?"

"Pig, pig blood!"

"Well. But why are you running away? A gentleman avoids the narrow path."

A gentleman should walk on the main road.

Qing whined again as she wrote the text.

This was a characteristic of someone who learned things poorly.

"That, that…"

"Okay. Answer carefully. I'm holding a knife."

"that……"

Udam hesitates and avoids answering.

That was when.

"What's going on!!"

A powerful momentum that quickly approaches with a loud roar.

Qing immediately raises his sword.

Bang!! The strong energy collides with the strong energy, flashing and bouncing up in the dark.

Even if Qing's strength was beyond human, he was helpless against the fundamental rules of the world.

For a woman, she was tall and has a lot of body fat in her upper and lower body, but she doesn't have any flab anywhere else, so she was lacking in weight.

If you lack weight, gravity will also be lacking.

The blue was pushed backwards, drawing two parallel lines on the floor.

Even as he was being pushed back, he fiercely swiped at the enemies who had rushed in.

But first, the guy was wearing clothes that were covered in a lot of blood, and this guy's entire top was soaked red.

Need more confirmation?

The blue tramples the ground and changes direction immediately.

The sunset-colored starlight draws thick lines, embroidering the world with the flowing trajectory of a sword.

A line running horizontally outward from the blue.

The expression on his face was becoming stiff.

A ray of life flashed in his eyes, and he pulled the handle back, and a red glow appeared on the withdrawn blade.

A blatant attempt at counterattack that ignores defense.

The corners of his mouth are long and thin.

Come. Are you a fellow traveler? Let's die together?

Okay, let's die once.

The Qing Qing energy in him grows brighter with a more brilliant light.

I put one hand on the handle and pulled it behind my back-

The compressed muscles of the blue exploded, drawing a huge semicircle with the force of a cannonball fired from the blade.

The guy quickly changes his posture.

The man took a stance in which he would respond with a stab, signaling her to back off if she didn't want to die with him, or perhaps a test of courage.

But, if it continues like this, it looks like it will be torn in half with one hit.

So, I had no choice but to change my position and block it quickly.

Taang!!

The guy was thrown out with a loud noise.

It penetrates the wall of the house, causing the wall to crumble and dust to rise.

Ah, the blue figure appears through the dust.

The bloody man's eyes open wide.

Qing's left hand swings wildly like a meteor shower towards the man who was hastily taking a stance.

A handful of dirt mixed with pebbles, as if it had been swept from the ground, hits the man's face before the sound.

Just then, he shot into the wide-open eye socket.

"Kwaaak!"

If dirt gets into your eyes, it hurts a lot.

Because dirt got into my eyes.

Don't you understand what I'm saying?

If you put dirt in your eyes right now, you will understand.

A bloody man, momentarily blinded, swung his sword in all directions, screaming, shouting, or more accurately, both.

It was a good attempt.

Qing was watching from a distance.

"Huh, huh, where are you! This vile thing!"

"What's so mean about fighting? Then why don't you just throw dirt at me too?"

The man forced his eyes open and glared at Qing.

The reason your eyes are twitching and twitching was because you are forcibly ignoring your instinctive command to blink quickly, saying, "There's dirt in here. Blink quickly."

"You don't know who I am! I'm none other than Sotalmyeongdo Osanchu! My father was none other than Talmyeongdo Odaean! Are you ready to take responsibility for the consequences?"

"Talmyeongdo!"

Qing shouted with a strangely excited expression.

Ah. It feels completely different when you know what you're saying and when you don't and just go along with it.

Qingdo now knows about the very, very famous hemp seed.

Because after the disciple who always charged without looking back burned down the Lulin Forest, Ximensurin was worried that he would suffer great harm, so he told him to memorize the dangerous Madou.

Talmyeongdo? I said it was Hyeon-gyeong's great horse head.

Even if he was the most evil of the demons, would he raise his own children as demons?

Then isn't he just an abandoned child?

Or did he teach his son to live like that because he lived a surprisingly good life by killing people with a marijuana plant?

"Ugh, okay. So now you know who you've messed with? Back off now—"

"Wait a minute! Do you know who I am?"

He stopped at the mistake.

"Why, if you're going to claim that you also have Hyun-kyung Gosu as your backer—"

"No. You don't even know who I am, so how would you know who your child's enemy is? Do you know my face? Do you know my name? If you don't kill me now, won't it only cause more trouble?"

"uh?"

"If you kill that guy, Talmyeongdo will be like a father's instinct. Oh, it seems my son was dead. And I suddenly know who killed him! My child's enemy! I'll kill him! Is that what you're saying?"

"That's because my brothers are outside…"

"Among you, was there a master as good as Unrestrained Realm? There's only one Unrestrained Realm master, and a first-class… no, that's enough. Is there really a need to insist on a first-class master? Can you really beat a Unrestrained Realm master?"

Osanchu's eyes twitched.

It was a physiological phenomenon that tears flow down, but the timing was truly exquisite.

"That, that's right. You cowardly bitch! Reveal your name! Are you planning to hide your name while dividing life and death!?"

"What are you talking about? Are you trying to tell Dad?"

"That's not it! Isn't this a basic example of unmanned operation?"

"Uh. Are you really going to teach me? Then I'll have to kill you. Are you really going to reveal my face and name?"

"Wait a minute! Give me some time to think about it."

The more I try to adjust my words, the more amazing it becomes.

Qing was dumbfounded, but at the same time curious about what will happen next, so she adds to the rhythm.

"What are you thinking about?"

"Well, even if you reveal your identity, there's a chance I'll run away, so I need to think about how you'll react before I can decide whether to make you reveal your identity or just ask for forgiveness and end it here."

"What? Why are you asking for forgiveness? What did I do wrong?"

"Wait! I'm thinking!"

No, what's so confident about this?

As Qing, whose speech was interrupted, opened his mouth in shock, Osanchu, who had been mumbling to himself, finally nodded.

"Good! Reveal your identity! And then kill me with all your might!"

"Ha. Why me?"

"Are you scared now?"

No, are you scared here?

Qing was amazed by the mysterious eloquence and eventually nods.

"I can't help it. Now, don't be surprised when you see my face."

The moment Qing raises her hand to walk the veil-

"Dead!"

Osanchu steps on the Jin-gak and advances the Tao.

And from the tips of Qing's long, thin fingers, a single black ray of light rises.

Heavenly Demon Death Ray!

…not this Cheonma Explosion Site!

The black straight line suddenly touches Osanchu's instep, causing a pop, the flesh bursting and blood to fly out.

The Heavenly Demonic Art was too advanced a skill for someone just a beginner to use.

So, it doesn't have the power to explode the bones and flesh, but rather just leaves the bones behind and the flesh bursts deep inside.

Thanks to this, the bone and flesh of the instep are literally separated and the foot rolls on the floor.

"Ahhh!"

"No, am I an idiot? Who would have thought I wouldn't know how to stall for time until the dirt in my eye fell out?"

Qing was confident that he can compete with any big shot in the world with his dirty tricks.

So, what I'm saying was that I'm not so naive as to fall for such basic time-wasting tactics.

"You pretended to be fooled, so what are you talking about? If you're going to launch a surprise attack, you have to be quiet. 'I'm dead!' Why are you telling me you're launching a surprise attack?"

"Ugh, you bitch! How dare you do this!"

"What are we going to do about this?"

Qing aims the Moonlight Sword, then bursts out laughing and instead extends his left hand forward.

"Okay, I only shot with my index finger earlier. Next time, I'll shoot with all five fingers? Are you confident you can dodge all five lines?"

