\chapter{Every Treasure Has a Sad Legend (1)}

The noisy atmosphere of the restaurant suddenly became as quiet as a remote forest.

The scholars, who had no particular talents other than their tongues, were furious and tried to glare at the ruffians who dared to block the good words of the sage, when, uhm, never mind.

At first glance, he looked like a thug.

From his disheveled hair that was completely unkempt and spread out in all directions, along with his dark skin, he was clearly a barbarian without any roots.

They also looked very vicious.

Of course, the scholars knew from the words of the sages that they should not overlook injustice.

But Confucius said, avoid those who defecate in the middle of the road.

The teaching was that foolish and incompetent people will never change, so don't lecture them and just let them live as idiots.

So, as the most learned one among the scholars, Qing disobeyed the words of Confucius and looked at those scoundrels.

\textit{Are they bad guys?}

\textit{But do we have to kill all the bad guys?}

\textit{Besides, this time, isn't it clear that our side was at fault?}

Even though the restaurant was all about eating, drinking, and talking, the volume of voices might have been excessive and made people frown.

Even a villain might have just wanted to eat in peace.

If she insist on going against their will and rushing in, wasn't that not being a hero but an excuse for murder?

"We've caused trouble by making a fuss. I'll make amends, so please calm your anger"

Qing first apologized somewhat politely.

However, Confucius was not a weak scholar.

In those brutal times, he was a warlord leading disciples, a strong man who freely wielded the eighteen classical weapons of ancient martial arts.

The eighteen weapons are bows, crossbows, swords, sabers, great swords, spears, short spears, hooked spears, crescent blades,  shields, axes, hammers, whips, clubs, staffs, nets, knives, and bare hands (these weapons vary slightly from region to region).

Would it really be the case that a Master of not one, but eighteen weapons would tell people to avoid their opponents simply because they were strong?

Confucius's advice to avoid madmen was not a cowardly excuse.

It means that you should ignore a peron who won't listen to reason because you won't be able to communicate with him no matter what.

The thugs' momentum soared to the sky.

Usually, a cultured person thinks that if the other person bows first, he or she has made a concession.

But those illiterate idiots thought that the other person were scared and submitting.

This was an undisputed truth that idiots were all the same, not only in Zhongyuan but also in the East and the West, and in the past and the future.

"Kuhaha, this elders' moods have already been ruined. Even if you regret it now and apologize, will that be enough? Wouldn't a more sincere apology be needed?"

"What do you mean with a sincere apology?"

"You can makes these elders happy with your body. Why are you so wrapped up, you little bitch? First, take off those cumbersome clothes and come over here and pour me some drinks. Hehe."

\textit{What? Are you a man who enjoys the pleasures of life?}

Qing held back her anger once more.

The character for patience (忍) was a combination of the character for blade (刃) and the character for heart (心).

It meant that you have the heart of wanting to stab someone right away.

So, the meaning of 忍 included not only patience but also the meaning of cruelty and ruthlessness.

"My companions were a bit excited and raised their voices, but a meal was supposed to be enjoyed with loud voices and chatter. Why would you suggest of such outrageous things?"

"This bitch doesn't seem to understand the situation. We're the kind of people who get goosebumps and lose our appetites just from hearing people reciting Confucius and Mencius. You've completely ruined our meals."

"So?"

"Do you know who we are? We're the Three Evils of Bingzhou who could make even the fittest men pee their pants."

\textit{Oh, isn't this the first time this has come out in a long time?}

Qing counted down. Three, two-

"The Three Fiends of Bingzhou!" "The Three Fiends of Bingzhou!" "The Three Fiends of Bingzhou!"

Judging from the fact that roughly one in three shouted their name, they seemed to be quite famous.

And with 'fiend' attached to their title, there's no way they're proper persons.

Qing smiled at him.

"Have you ever heard this saying? 'When you go out into the martial arts world, be careful of the elderly, women, and children'"

"Hahaha! You're saying that you're some kind of peerless expert… Uhm… Hehe, you should have said so."

Twinkling starlight.

The starlight that descended upon enlightenment manifested.

"Get on your knees, you little shits."

Qing sighed deeply.

\textit{Why on earth?}

\textit{I shouldn't have asked nicely, yes?}

\textit{It's funny because I'm a master, right? Otherwise, what would happen?}

\textit{These are bastards who tell you to take off your clothes and pour the alcohol.}

\textit{Even if you cried and begged for forgiveness, would they have let it go?}

"Right. Do you have anything to say?"

"We were wrong to not recognized…"

"Does it matter whether I'm an Expert? What if I wasn't? Why couldn't you understand when someone speaks kindly? I said I was sorry. What, did the scholars infuse their voices with Inner Qi? They're not even particularly loud. Is that something to apologize for in the first place?"

"That's…"

Qing sighed deeply in front of the three people kneeling down.

"Come to think of it, you didn't even know who the expert was, and you just kept on acting like that, so if you die, it'll just be a natural death. Even if it wasn't me, you'd probably end up messing with the wrong person and get in trouble. Well, let's just each of you leave an arm for the life lesson's tuition."

"Oh my, Great Hero, if a warrior loses his arm…."

"You said you're The Three Fiends of Bingzhou? How many of bastards with 'Fiend' on their name are actually normal? And what if the rumors spread, 'That Heavenly Blossom Sword let those bastards go free'. Do I really want to bear that resentment later? Even if I don't kill you, those people you wronged will sleep soundly if they know at least the Three Fiends got their arm taken."

Heavenly Blossom Sword. The Three Evils of Bingzhou's eyes glinted.

'If it's the Heavenly Blossom Sword, isn't it in Early-Stage Transcedent?'

'If the three of us make a surprise attack, it seems like we could win.'

The Three Evils of Bingzhou secretly made eye contact with each other and opened and closed their mouths invisibly.

However, Qing could read the air.

It's not the metaphor of being good at reading the atmosphere, but rather mastering fluid dynamics with sensitivity and being able to grasp all movements within a narrow range.

\textit{Why can't you be grateful?}

\textit{Can't you just leave one arm behind?}

\textit{If you've been doing bad things so happily, you'll lose an arm. It's a very cheap price to pay for all the things you've done, so why not just give me one arm and go?}

It was the moment when Qing let out a deep sigh again.

"Kill her!"

As if kneeling down was for momentum, the guys shot out like arrows at a fairly fierce speed.

The gleam of metal.

In an instant, the Qing's form splitted into eight separate afterimages, each jumping, walking, floating, and doing somersaults in each direction.

Wave Treading Subtle Steps was good in many ways, but it had the disadvantage of being very dizzy.

It was a truly real-life method of folding space by twisting the energy of nature.

What others might saw as a cool skill, to Qing, it's a dizzying experience, as if the world was unfolding in all directions and she's falling in all directions.

Since her body was beyond human, it can be used without any burden. If it were a normal person, they would immediately stagger, vomit everything they ate, and suffers from extreme motion sickness.

But Qing's body endured.

Qing, who had cooly appeared with her back on the enemy, stretched out her hand.

The back of the head of one of The Three Fiends of Bingzhou, whether first, second, or third, was suddenly grabbed by a thin, long finger.

The three of them planned a surprise attack, but one of them immediately turned his back and ran away, but was caught.

Qing's ferocious strength grabbed the back of the man's head and swung him backwards.

Boom! The solid kitchen floor shattered.

The bastard's leg snapped in a peculiar direction, and a loud scream erupts.

One man down.

Bam, Cheong's body stretched out, dust fluttering as she belatedly turned.

The right and left hands of the Qing were bent like sickles and pulled behind the sides like taut bowstrings.

And then, Qing's arm that was thrusting between the two suddenly stretches out.

The palms of her hands, with their slender fingers spread out, dug deep into the lower abdomens of the two men.

\textbf{White Hand Demonic Art. First Movement: Absolute Joy.}

To cut off the enemy's lineage and laugh with joy.

As if by agreement, the two men stood side by side, knees down, holding their stomachs, and gushing out red blood.

Qing shook her hands in the meantime.

"Anyway, one of them ran away without any character. He has no conscience, no loyalty, and he doesn't even have any skills. Now, is there anyone among you with a wide knowledge who can explain to me what kind of people these Three Fiends of Bingzhou are?"

"They are vicious thieves!"

One had a twisted leg and two were rolling on the floor, spurting blood.

If they hadn't been neutralized, it would have been different, but at first glance, it looked like there would be no repercusions, which gave people courage and made them want to report it.

Originally, the Three Evils of Bingzhou were the elite of the Northern Army, but their plundering was so brutal that they were expelled from the military.

You might wonder if they should be expelled just for showing off robbery, murder, rape, and torture to the northern barbarians, but the problem was that these bastards committed the same acts in Han villages near the border.

Thanks to this, they are wanted by the military and have a large bounty on their heads.

So, they are people who live near the border, moving between the country's territory and the barbarian's territory, avoiding tracking or something.

Qing tilted her head at this.

\textit{These guys lives near the border to avoid being tracked?}

"What? But why did you crawl all the way to Taiyuan? Are you determined to die? If that's your wish, I can grant it."

"Now, wait a minute! We didn't just come down here!"

"What if you just don't come down?"

"That is… if you spare my life, I will tell you as much as I want. It was a story that will probably interest Great Hero as well…"

"I don't care. Is that the end of your last words?"

At that moment, one of the guys shouted in panic.

"No! That's it! A treasure map! A treasure is hidden here! We came down here to find it, and if you spare us, I'll hand over the map!"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Tian Yuxue focused on interpreting the treasure map for over two months.

And that obsession eventually paid off.

He have succeeded in narrowing down the list of strong candidates for the treasure spot to five.

Now all that remained was to search these places in person.

"Master, I'm back."

"Oh, you're here? Hmm? What about those guys you brought in? What's wrong? Why are their arms and legs folded like that?"

"But they're just beast. Those things barely worthy of being called human."

"If that's what you're saying, then that's what it's. Well, more importantle."

And just like that, the Three Fiends of Bingzhou became 'those things'.

However, Tian Yuxue was also a person who believes that there was no need to show any mercy to non-human.

And he also had absolute faith that the good disciple would not catch and harm innocent persons.

So she did a good job.

Rather than that.

"Khuh, I've finally, finally finished interpreting the teasure map! There are five locations in Zhongyuan that match the map, so let's start from Liaoning and circle the Zhongyuan, one by one."

"By any chance, iss there a place called Jimo County in Shandong Province among those five?"

"Huh? How would you know that?"

Qing sighed deeply at him.

"It doesn't say what's buried in that map, does it?"

"I don't know, but isn't it true that something great was buried there, so it must be hidden so tightly?"

Qing then gave the answer without a second thought.

"I heard it's called the Essence Absorption Demonic Art\footnote{吸星大法; Xi Xing Dafa; Star Absorbing Technique. Originated from Jin Yong's novel 'The Smiling, Proud Wanderer'}."

\vfill
\begin{lstlisting}
	The chapter title is a reference to a line in K-drama 'Iris' (아이리스)
\end{lstlisting}