\chapter{Every Treasure Has a Sad Legend (8)}

In fact, it's difficult for human thoughts to go beyond a certain range of thoughts.

So what I'm saying was that people's thoughts are all the same.

Of course, there are people who can think of out-of-the-ordinary ideas that go beyond the normal range, but they are so rare that they are called geniuses.

So, the idea of ​​asking someone who knows Laosan well about geography was not particularly surprising.

Rather, it could be said that it was a very late idea compared to the great knowledge of the professor.

It was a thought that occurred to me after I went into the mountains and wandered around for a day and thought, 'Ah, this isn't it.'

Well, that's because I'm in a hurry.

Treasure hunting was the most evil thing in the world.

It can be said that he was so determined to show off his skills in front of his disciples that he was completely out of his depth.

Anyway, this was not a special idea.

Even if you haven't learned the saying of Confucius, Mencius, and Xunzi, "If you don't know, ask," this was common sense that anyone who isn't a timid person (a pitiful perceptive person) or an anti-intellectual (a fool) knows.

So, this was an idea that even those with little experience in learning can easily come up with.

How easy would a remote village be for those guys?

Of course, the people of these fortified, outlying villages are not fundamentally good.

Just like the wall surrounding their village, the mental wall that separates people from outsiders was also high and strong.

But was that a reason to be wiped out?

No, that's not it.

"Hmm……."

Qing lets out a cold groan.

Of course, he didn't just groan.

The Moonlight Sword drew a crescent moon stuck to the ground with its powerful force, and naturally separated the ankle of Osanchu, who was in its path.

"Eww!"

Osanchu, tightly bound by the Divine Thief Vision Binding Technique, cries out in pain beyond the gag.

He lifts the separated foot with the tip of his sword and then skillfully swings the sword to send it flying.

As a result of Divine Thief's sword training, Qing was a prospective Divine Thief who can use the sword as if it were his own hand.

The foot of the falcon that flew in a parabolic arc.

It fell into place among the gently piled corpses, and it felt very natural, as if it had always been there.

If you add one lost foot to a pile of corpses, wouldn't it be like adding sand to a sand mountain?

"This."

But even Tian Yuxue's words have no power.

Qing makes an excuse.

"I think you're trying to run away."

Osantu was already tightly bound with one of his feet deeply wounded.

What about running away?

If he ran away in this state, it would be a truly amazing and surprising feat that should be seen, even if only out of curiosity and surprise.

Oh my! The Osanchu does a pretty good job of imitating a shrimp that has fallen to the ground.

I would say it's a very surprising individual skill.

Qing looks down at the sight indifferently, then looks back at the pile of corpses that were once the villagers.

Osanchu and his brothers knew nothing about Mount Lao, so they decided to ask him if they didn't know.

However, asking when you don't know something requires a lot of courage.

So, even the various thinkers of the Hundred Schools of Thought went around preaching to the world that if you don't know, please ask, and that it's absolutely not shameful.

Because the very state of not knowing was shameful.

That's why I'm asking you this.

Osan Chugwa and his younger brothers endured such humiliation and asked about Mount Lao.

But unfortunately, I came to the wrong village, and the surrounding area was full of rice paddies and fields.

How dare you not know?

I asked you at the risk of humiliation, and you dare say you don't know?

And how was it that no one knows about the mountain when it's so close?

Do you know who was disabled?

Come on, you're making such a fool of me!

I also relieved some of my sexual desires that I couldn't resolve because I was in a hurry.

Even if there had been a skilled hunter, the results would not have been much different.

Because good information should be kept to myself.

Whether he had been offered a volunteer guide by the hunter or had simply been informed, he was doomed to die either way.

And then what?

I don't want anyone to know that I stopped by and got information.

And the dead do not speak.

Just like this pile of corpses that were just thrown together and piled up, tangled, folded, crushed, and broken, and yet just piled up without saying a word.

"Tsk. Those little things."

Tian Yuxue clicked his tongue.

For a long-time Zhongyuan person, this isn't something that would be that shocking.

It was a particularly familiar sight to Divine Thief, who had been carrying around (stealing) particularly dangerous treasures.

This was why Divine Thief steals treasure.

The danger was that greed itself will only attract evil spirits who have abandoned humanity.

Bad guys can become even worse when they become greedy.

"I see some guys over there in that tile-roofed house cooking. Oh, it's past mealtime, so they're hungry. What are you doing? Why don't you go and make some food? Shouldn't you be the one making the offering?"

The disciple told me to go and cook some food.

Of course, Qing might not know what that means.

This was the teacher's consideration to tell you to go somewhere else so that he can take care of these guys.

Qing pretended not to hear and looked at Chen Changming for no reason.

"Oh. Changming'er? Did you hear that?"

"Me? I'm not your disciple, Master…."

"What are you talking about? You don't even bother to take care of the private offerings? How can you make the elder's stomach growl with this great disciple missing? When we get back, shall we gather under me and above you?"

The youngest sibling of the long-lived family, Qing-gwa, and the youngest sibling of the great disciple, Chen Changming.

If you bring them all together, it's the total gathering of the first and second great disciples.

Of course, even if they were called together like that, the atmosphere at the Shinnyeomun was not as serious as it always is.

We all chatted away, hahahoho, and thanks to our pretty youngest, Sasuk, we skipped work and had fun. But were you sad that you were hungry? I guess I'll say something like, "What do you want to eat today?"

"You bitch, I told you to cook some food, why are you just throwing it away? Is your butt too heavy to move?"

"It's a matter of internal discipline, isn't it? So, just take a look around and get some food."

"What was it?"

"Oh, raindrops!"

"No, do those damn raindrops only fall when the horse was about to turn?"

"Wow, I thought those raindrops were from someone pouring water on me. It looks like it's really going to pour. Master, you're taking shelter from the rain for now. I'll just finish up quickly and go. Jangmyeong, hurry up and make dinner."

Tian Yuxue sighs deeply at the bright voice that Qing-i was speaking.

"Don't worry too much. We've never even met before. Just handle it cleanly. Even if you feel a sense of relief from the needless bloodshed, those heinous actions will ultimately hurt you."

"Hehe. These guys were really vicious. Okay, I'll clean up after myself and then I'll go. It looks like it's really going to rain, so stay inside."

Qing pushes the teacher away with a laugh.

Of course, he smiled, but his eyes were filled with ominous colors.

Qingi Sotalmyeongdo Osanchu and his younger brothers were well-groomed.

For reference, the act of beating up a villain in Qing means breaking both his arms and legs with clubs.

This was because it can be neutralized cleanly, so they can't even run away, let alone do anything.

Only after Qing finished grooming him did he release Osanchu's gag.

"Okay, do you have something to say?"

"Hey, let's talk, let's talk. What do you want? If it's gold or silver, I have my checkbook. It's worth about fifty gold coins, but if you want, I'll add a few hundred more. Take it."

"Do I look poor when I look like this? I'm rich."

"So, what do you want? Well, how about Talmyeongdo? It's a peerless divine skill that created the masters of Hyeon-gyeong."

"I have several new skills, too. So many that I forget every single one I learned. When I go to bed, I kick the covers off and think, 'Oh, right, if I had used something else, I could have won easily.'"

Qing moves her body busily as she answers.

However, I don't know what it does.

Where would you get old blankets, grab each of them, roll them up, and tie them up with rope a few times?

For your information, since twisting rope was a daily life hobby of the common people of Zhongyuan, you can find ropes rolling around in bundles in every house.

"Why on earth, why are you doing this!? What grudge do you have against me? If you have a grudge against your father—"

"No, you were the one who suddenly threw the gun. And I didn't even know who you were, and what grudge do you have against your father?"

"That's my apology! I got so excited when I saw you trying to hurt my brother!"

He Qing stares blankly at Osanchu.

"Why did you kill the villagers?"

"My father doesn't know I'm here."

"Ah. A gag order? Then I should try gagging too."

"Why are you so vicious! I killed some of those wretched creatures. Oh. By any chance. Uh. This village was your hometown?"

"No. This was my first time here."

"No, but why!"

Osanchu bursts out in anger as if he can't understand.

I can't understand Qingdo.

Who on earth are the evildoers of Zhongyuan?

Why are you guys like this? What's the problem?

Was there any need to worry and groan about whether I should kill or save?

Because the way of thinking itself was different.

The Ximen Qing was the most peaceful and safest country in the world.

Murder itself was horrific, and it's a safe society where I cannot commit it or imagine others doing it to me.

But what about the central plains?

It was quite natural for a middle-aged person to stab someone to death over a minor argument, stab someone to death for a small profit, and turn into a robber, rapist, or human trafficker at the slightest opportunity.

Not the martial arts people, but the people of Zhongyuan. In fact, not only the people of the Zhongyuan, but all of humanity in this era was like this.

This was the lifestyle of a still uncivilized era.

If we look at the history of the world of Qing, it's still an uncivilized, primitive ancient time, with over a hundred years left before the concept of human rights even existed.

Qing asked, clicking her tongue.

"Okay. And that name tag? Do you have emergency supplies? I only accept advance payments. Miss, just hold on tight. I've finally given up."

Qing wraps another younger brother in a blanket, and then slaps Odubangjeong, who can't stay still, on the cheek.

Well, I was lying in bed with my arms and legs broken and kept turning over.

Because the pain surged from the broken area.

"There's no way I'd carry around a secret weapon so carelessly. It's in my head."

"In your head? Then I can just split it and take it with me?"

"If you promise to save me-"

"No, I'm not a cripple. My son died, and suddenly someone I know was wearing a name tag. Wouldn't that make Talmyungdo come after me and avenge my son?"

"Hmm……."

"Just call me Gugyeol. If you don't end it before I kill all your brothers, then there will be no more negotiations. I'll kill them all and bury them."

Osanchu cautiously opens his mouth.

But Qing doesn't seem to hear anything and just flutters around, unfolding a new blanket and laying it on the floor.

He became anxious about the mistake.

He said that there would be no negotiations if he finished talking to his younger brother, but he didn't show any signs of delay and just rolled up his blanket, so he didn't have the presence of mind to talk about twisting his neck.

"……so that I can take away ten thousand lives, I've called them all! I've called them all!"

"Um, red. Not really?"

"I've called everyone! Now then-"

"No. You said it was a divine technique. What kind of divine technique was this? Oh, was it by any chance a good spiritual technique? Try calling out some spiritual techniques."

"What the heck, wait a minute, stop, I'm calling you! The world just feels like it's going to be…"

Qing finished speaking with Awoo as background music.

The recitation of Osanchu's vows ended when he was tying a knot on the last brother's rope.

De-Brightness, red.

Demyungjeongsim, gold.

"Oh, gold. That's a good technique. As expected, I wondered how he got to Hyeon-gyeong. Internal energy was key, after all."

"What on earth does that mean?"

"You don't have to know. If you do, you'll get hurt, no, you'll die. I'll kill you."

Even Qing, who answered like that, spread out the blanket.

Osanchu was startled and screams at him.

Since all the younger brothers have been killed, the only person left was Osanchu.

"Why are you covering your bed? I already called you! I promised—"

"No. Why? You think I'll just listen to the spell and memorize it all at once? Can you do that? Should I try reciting my martial arts?"

"that……"

"Okay. Behave yourself. Oh, I want some kimbap. Make it for me when you get back. No. Um. Is there kimbap in Jungwon? I don't think I've seen any."

"What are you talking about!"

That's all for the small talk.

Qing puts the gag down very naturally.
