\chapter{After The Fire (5)}

The martial artists of the Zhongnan Sect had not merely come along because they had nothing better to do.

With the vast scale of their Daoist temple, there were always tasks to be done. If they took a day off, they would have twice as much work the next day.

However, the Sect Leader's statement that he was bored wasn't entirely wrong.

What dramatic events could possibly occur in the life of a Daoist temple?

Then, amidst such a mundane existence, the most likely candidate for the title of 'Most Beautiful Woman Under Heaven', the peerless beauty closest to being called 'The Most Beautiful Woman in the World', the Heavenly Flower Sword, had arrived. Naturally, everyone gathered around.

However, as history has proven, such idle curiosity often leads to great discoveries. The martial artists of the Zhongnan Sect who were present were given an opportunity to witness a great spectacle.

The Heavenly Flower Sword gazed at the Absolute Sword Wall for a while, then suddenly drew her sword and raised it high, as if pointing to the sky.

In that instant, the sword reached the sky.

It was just the image of a sword being raised high, yet everyone present knew it to be true.

A giant, it was a giant!

When a person becomes independent from the stars of the sky and walks on their own, they finally exist fully and achieve themselves. Thus, it is called 'achieving' (成), and they become a 'sage' (成人).

She was a fully realized being, seen through the eyes of children who merely followed the guidance of the heavens.

Naturally, they could only look up, lifting their heads high.

Because to them, she appeared as a giant whose end touched the sky.

Thus, the sword of a human pierced the heavens.

Because it was a human's, the blade did not shine, but its sharpness, honed by the heart, pierced into everyone's psyche, blossoming into a fear that felt as if their hearts were being split apart.

And finally, already, suddenly.

As Qing's sword returned to its sheath, everyone saw the image of a giant striking down with a sword, cleaving the cliff.

With that majestic strike, everyone held their breath, and in a world where only silence remained, the Heavenly Flower Sword exhaled deeply, 'Huuu,' and spoke.

"Fuck."

Huh? What did she say?

And then, she collapsed limply, like seaweed out of water.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The hottest topic that was setting the Zhongnan Sect ablaze was clear.

It was about the final words left by the Heavenly Flower Sword, who was now acknowledged as the 'Most Beautiful Woman Under Heaven' (since the Zhongnan Sect now accepted Qing as such) before she collapsed.

What could be the connection between the enlightenment left by Senior Celestial Martial Emperor and the word 'fuck'?

Moreover, the Heavenly Flower Sword was a woman, so she didn't even have a 'fuck'.

But to say 'fuck'?

How could that single word, 'fuck', be related to the giant's sword strike that reached the sky?

Some Daoists suggested that 'fuck' referred to the natural ascension of the innate True Qi, which always strives upward towards the sky, vigorously and ceaselessly.

Others speculated that she might have been about to say 'fantastic' upon enlightenment, but collapsed from exhaustion before she could finish.

However, it was too clear to be that. Anyone who heard it would agree it was 'fuck', not a cut-off 'fantastic'.

Or, perhaps, it was a terrifying thought, but maybe the technique left in the Zhongnan Sect was called 'Fuck'.

The Nth Technique of the Nine Swords of Solitude. Fuck.

The licentious conduct of the Celestial Martial Emperor, who embraced women wherever he went yet was never resented and was instead longed for as the best night of their lives, was as famous as his martial prowess.

Given his eccentric nature and the various outlandish acts he committed, it wasn't entirely impossible.

However, since the Heavenly Flower Sword was unconscious, the curiosity of the Zhongnan Sect's Daoists only grew like a snowball.

Thus, Qing regained consciousness on the third day after she had fainted.

Thanks to this, as soon as she woke up, or more precisely, as soon as she regained consciousness even before opening her eyes, she was hit by a terrible pain that felt like her insides were being scorched, causing her to instantly open her eyes and sit up, screaming.

"I'm hungry! Food!"

Startled by the commotion, Seol Ri-ri, who was beside her, looked at her with wide-open eyes.

"Are you okay?"

"No, I'm not. It feels like my back and stomach are stuck together. Is there anything to eat? Anything?"

"Yes."

It was the first time a single syllable had ever sounded so harsh.

She doesn't even carry any food around with her.

She's really good for nothing.

But how could Seol Ri-ri, who didn't even have a penny to her name, carry food around with her?

"Ugh, why am I so hungry? I know I collapsed after seeing the Absolute Sword Wall, but how long have I been lying here for this to happen?"

"Three and a half days."

"Gasp. I haven't eaten for three days?"

Qing was horrified.

If it had been three days, that meant she had missed dinner that day, breakfast, lunch, and dinner the next day, and breakfast, lunch, and dinner again on the third day. Assuming she didn't know what time it was now, that was at least seven missed meals.

The amount one could eat was limited, with only three chances a day, and she had missed seven of them!

And that was the bare minimum of seven meals.

What time, what time is it now?

"It has just passed the hour of the dog."

"Gasp!"

The hour of the dog meant it was past eight in the evening, so she had missed both breakfast and lunch today, making it a total of nine missed meals.

Moreover, meals provided by the Zhongnan Sect.

How could a sect that was rich enough to gild their roofs with gold possibly serve ordinary meals?

How, this is just, this is just too much.

That old man, the Celestial Martial Emperor, I will detest him.

"Are you okay?"

"I'm so hungry I could die."

Then, Seol Ri-ri shook her head.

"They said it would be difficult to circulate your Inner Qi. Because your blood meridians are all damaged."

"My meridians? Huh? It feels fine. Heueuk."

Thoughtlessly trying to circulate her Inner Qi, Qing immediately coughed up air from her lungs and rolled her eyes back.

In that unprepared state, the horrific pain of tens of thousands of needles simultaneously piercing her internal organs rushed in all at once, causing her to immediately lose consciousness.

And a little while later.

"I'm hungry! Food!"

"Are you okay?"

"No, I'm not. It feels like my back and stomach, wait, huh? What's this? This conversation… It feels like we've had it before, what do you call this? Déjà vu?"

"I don't know."

Seol Ri-ri only answered questions.

At that, Qing frowned deeply.

"No. I don't mean that. Ugh."

No, right now, how can my meridians be so messed up that I lose consciousness just from circulating my Inner Qi for a second. Ugh, uuuuugh.

The thought of that pain made Qing shudder.

But that didn't mean she was too worried.

After all, she didn't know if it was the Celestial Martial Emperor's dying thoughts, some kind of mental parasite, or, as the old man claimed, an illusion of the Celestial Martial Emperor that she had interpreted and created herself. Since I made it, shouldn't it be called the… Mucheong Emperor or something?

Mucheong Emperor. Simmered Radish would be delicious. Hmm. I want to eat some refreshing Radish Kimchi.

If I slurp some cool and refreshing Radish Kimchi Noodles, mmmm…….

"Ugh. I'm so hungry I could die."

Being hungry makes me think of all sorts of things.

Anyway, Qing wasn't too worried about her meridians.

After all, if the Mucheong Emperor said she would be a cripple for the time being, that meant she would be fine after some time had passed, didn't it?

And Qing was already the strongest under heaven without using her Inner Qi, the pinnacle of the human body as a female.

More than that, food, food was urgent!

I thought about Radish Kimchi and now I really feel like I'm going to die.

Fortunately, there was leftover rice in the temple, so they mixed it with leftover vegetables and sesame oil, creating what Qing considered to be a perfect bibimbap.

For reference, this was not a part of Zhongyuan' culture, so they had just made an excellent dog food by mixing all the leftovers of a proper meal.

She crammed spoonfuls of it into her mouth, cheeks bulging.

Tajung Jinin, the Sect Leader of the Zhongnan Sect, watched this and thought, 'What? Was the Heavenly Flower Sword a disciple of the Beggar's Union, not the Divine Maiden Sect?

Have I been mistaken all this time?

Even a disciple of the Beggar's Union wouldn't eat donated food so greedily and yet deliciously.'

Still, Qing was a beauty that could be discussed as being under the heavens.

If a less attractive woman had eaten so sloppily, like a beggar or a starving ghost, it would have been off-putting.

But because her beauty was so outstanding, one would think, 'The child must have been very hungry. But she eats so heartily. It seems like her body hasn't been harmed much, which is a relief.'

This is the way people are so deceitful.

"Haaah. Now I feel alive. Thank you for the meal."

Qing patted her belly, which looked like she was about seven months pregnant, and let out a happy groan.

Seol Ri-ri, who was still looking at her with an expression that seemed to ask if she was seeing things correctly, continued to stare intently at her wondrously inflated stomach.

Tajung Jinin was more interested in other matters.

"Yes. Since we were in a hurry, we could only prepare a humble meal with leftovers. But since you ate it so deliciously, it pleases me as well. So, I heard you gained great enlightenment from looking at the Absolute Sword Wall."

"Hmm."

Qing briefly pondered over her conversation with the Mucheong Emperor.

Was there really any enlightenment to speak of?

"Ah. Right. The Seventh Movement of the Nine Swords of Solitude, Jian Yue Wang Zhi."

"Seventh Movement?"

Tajung Jinin's face bloomed into a childlike, bright smile.

"Indeed. If Mount Hua has the eighth movements, it's only right for the Zhongnan Sect to have the seventh. Yes. That is how it should be."

If the Celestial Martial Emperor had known, he would have shouted and beaten him, saying, 'You Daoist bastard, spouting nonsense about numbers.'

But what could the ascended Celestial Martial Emperor do?

"But Jian Yue Wang Zhi. Seeing the Moon and Forgetting the Fingers. Isn't that a phrase from a Buddhist scripture? Let's see, was it from the Diamond Sutra?"

Qing just sat there quietly.

When you don't know, it's best to stay still.

Despite being a fake Daoist full of worldly desires, Tajung Jinin correctly identified the name of another religion's scripture.

The Diamond Sutra explains, 'If someone points to the moon with their hand, you should naturally follow the finger to see the moon.'

This was a phrase, a teaching, that likened the finger to Buddhist scriptures.

It taught that scriptures were merely a tool to reach Nirvana, so one should not become obsessed with the scriptures themselves and miss true enlightenment.

"But why did he give it such a name?"

"Ah. That's because."

This time, Qing knew the story, so she eagerly chimed in.

It was a human instinct to want to show off when you knew something others didn't. After all, there's nothing that people like more than showing off their knowledge.

"He said that the path led by the starlight is not the goal of martial arts, but a process to reach oneself. He said one must overcome their nature, handle their heart with their heart, and establish their center with their own sword."

"Hmm. Seeing the Moon and Forgetting the Fingers. Overcome the self to control the heart, and establish the center with the sword. Geukgichisim Geomjeongjungwon."

Tajung Jinin's expression was that of someone who was about to sneeze, a look of someone who was caught in a state of ambiguity, not quite understanding something.

"Still, I understand one thing. A sword that no longer shines with starlight, but is wielded with the heart, is a human's sword. Indeed, it is the realm called the Heart Sword."

"Heart Sword?"

Qing made that expression.

Then, Tajung Jinin smiled like a true Daoist.

"I do not know either, so I cannot speak as if I know what I do not. But our Youngest Sister will surely reach it. You have already shown it once, so even if you do not know it now, it will come to you as great enlightenment later. Hmm, something seems to be coming, but not quite. I should reflect on the words of Senior Celestial Martial Emperor again."

"Yes. Please do."

At that, Tajung Jinin rose from his seat.

Just as he was about to leave the dining hall, he suddenly asked as if he had just remembered.

"Ah. By the way. Before you lost consciousness, you said 'fuck'. What did that mean?"

"Ah. Did that leak out?"

Qing scratched the back of her head with an embarrassed expression.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

According to the elder of the Zhongnan Sect's Medical Hall, it was closer to a fortuitous event than an injury.

Every single one of her Eight Extraordinary Meridians throughout her body was thoroughly shattered, without even the slightest gap, but they were neither severed nor twisted.

"You will feel a lack of energy since you've lost a lot of Inner Qi, but your blood vessels have become wider and stronger, so it could be considered a fortuitous event. Inner Qi will accumulate again as long as you are alive, after all."

"Hmm. I see."

It seemed that an ordinary martial artist would have lost quite a bit of Inner Qi.

However, in Qing's case, rather than losing, she had gained some.

The Heaven-Shattering Demonic Qi was pretending not to know anything, but a very small portion of it had become able to move around freely.

The Medical Hall Elder looked at Qing with the eyes of a grandfather looking at his granddaughter and smiled.

"However, if you add a little bit of elixir, it might lean a little more towards a fortuitous event. Here, the Sect Leader told me to give this to you. It's called a Purple Night Pill."

"Wow! Purple Night Pills!"

Qing first acted surprised, but then, hmm, something felt a bit off.

What is this? Did I misunderstand something?

"Eum. Isn't the Purple Night Pill a legendary elixir of the Mount Hua Sect?"