\chapter{After The Fire (8)}

When a martial artist's realm reaches a high level, they reach a state called imperviousness to heat and cold.

This refers to a state where the body is no longer harmed by cold or heat.

It means that even when it's cold, the body temperature doesn't drop, and even when it's hot, the body temperature doesn't rise, thus the body is not harmed.

This is the constancy of the body, and in martial arts, the 'mind' in the commonly referred to 'unwavering mind' refers to both the mind and the body. Therefore, it is a natural phenomenon for a master to reach imperviousness to heat and cold.

However…

Just because the body is not harmed by cold and heat doesn't mean that one does not feel cold or heat.

Even a master feels cold when it's cold.

Likewise, they feel hot when it's hot.

Even in Qing's house, where ice storms raged in winter, her automatic defensive Qi preserved her body temperature, but she still felt cold. So, she would shiver and wrap herself in her specially made double-layered blanket.

Since body temperature was preserved, wrapping oneself in a blanket was enough to feel warm, so if one could maintain their body heat, they would quickly feel comfortable.

However, while cold could be easily warded off by putting on more clothes or using a blanket…

Heat was a different matter.

Until now.

Now, the Pathetic Inner Qi, the Pathetic Arts, arrives!

It will show you pathetic coolness!

…I found the answer! But why can't I use it!

It was clear that the wife of Mr. Kim, who died without being able to eat seolleongtang (ox bone soup), would also be heartbroken in heaven.\footnote{운수 좋은 날 (One Lucky Day), 1924's Korean short story}

Unable to bear it any longer, she tried to carefully circulate her Inner Qi, thinking maybe it would be okay if she slowly activated her Pathetic Arts. But then she almost died, ha, ack.

Qing drooped like a dog in the middle of summer.

In fact, it was the end of August, so the extreme heat had actually subsided a bit.

Nevertheless, Qing felt hotter than in midsummer.

This was because the Ice and Snow Arts had a minor side effect.

Due to the mysterious effects of the Ice Crystal, the owners of the Ice and Snow Arts became less sensitive to cold.

Meaning they didn't feel the cold.

But conversely, they became more sensitive to heat.

However, what need was there for the owner of the Ice and Snow Arts to go down to the hot southern lands?

As such, in the North Sea, the Ice and Snow Arts was a perfect, flawless Divine Art. But in the martial world of Zhongyuan… Ugh, wow, it's so hot I can't breathe…….

In truth, if she couldn't do it, someone else could.

There were two people in the carriage, and both could use the Pathetic Arts to create a cool breeze.

So, Qing spoke softly and kindly to Seol Yee-ri, who was sitting in a lotus position across from her, diligently circulating her energy.

"Hey, Yee-ri. Can't you use the Pathetic Arts for a bit?"

"Yes."

"So you can't?"

"Yes."

Qing's forehead bulged with a vein.

Seriously, why isn't this bitch using her cold air when she's hot too?

It wasn't as if Seol Yee-ri, who originally felt the heat a lot, didn't also have the Ice and Snow Arts.

So, Seol Yee-ri was sweating so much that one could have mistaken her for a human waterfall, with sweat dripping from her chin at a rapid pace.

She looked like someone who had been in an extremely hot sauna for about three rounds of an hourglass, sweating profusely.

Yet, even in that state, she just kept sitting in the lotus position, circulating her energy.

This made Qing feel resentful.

Since when had she been so diligent in her Inner Qi cultivation, acting all serious?

I fed her, clothed her, bathed her, put her to sleep, and even taught her martial arts and fed her elixirs. I've done it all!

Is what I'm asking for even that much?

I just asked her to keep me cool.

Hmph. She's just acting all diligent, saying she's training.

Let's see how long you last.

In Qing's view, she wouldn't last long anyway.

Except for meal times, she had been circulating her energy for eleven hours a day, all day long.

No matter what, you have to do things in moderation. If you keep sprinting at full speed like that, you'll quickly burn out.

That was what she thought. But a day passed, then two, and they slept in Seokcheonhyeon on the third day, Anganghyeon on the fourth, Pyeongrihyeon on the fifth, and arrived in Hubei Province on the sixth day, staying in Juksan.

On the seventh day, they reached Banghyeon, passed it on the eighth, and arrived at Heungsan on the ninth.

Their journey was set to reach the Divine Maiden Sect tomorrow night, exactly ten days later.

And Seol Yee-ri truly hadn't rested for a single day. Sheesh. What a stubborn bitch, utterly useless and only knowing how to be persistent.

I should have known when she kept walking, staggering even when her muscles were melting and her bones were cracking.

I should have just grabbed her and shook her until her tears fell out when I couldn't feel any pain.

It's annoying that I can't even say anything.

She's just gonna say she's training, so what can I even say? I can't just tell her to stop training and make me cool by blowing ice at me. Can I?

In my hometown, that would be like telling a friend who's studying hard for exams, causing their nose to bleed, that you're upset they aren't playing with you.

But then, why the hell are we even traveling together if this is how it's going to be?

Isn't this annoying if we're coming all the way here, on a trip, together just for her to study?

Can this even be called companionship?

In fact, for this reason, from the fourth day onwards, Qing had completely given up, thinking, 'Fine, you train, and I'll do whatever I want'. It was fortunate that there were Jongnam Sect martial artists assigned to escort them.

Among them, Daoist Pilmu, a first-generation disciple of the Jongnam Sect, had met her several times at the Dragon and Phoenix Assembly.

After all, he was always sitting in front of Changbin.

Changbin's introduction was exactly like this.

'This is Pilmu, Jongnam's…… well, the one, no, I mean, I, that is, me, the younger brother I cherish the most…, nononono, of course I also cherish Young Lady Ximen, it's, uh, that's not it. It's not a matter of seniority……'

The pet had come of age and rebelled, not even listening to her anymore. Moreover, it had forgotten its duty as a pet, so it was just a beast, sweating profusely.

So Qing had no choice but to turn her attention to other members of the group.

What Qing noticed was horses.

Come to think of it, I don't know how to ride a horse, do I?

Horses are convenient.

Of course, they would be. They have four legs that walk for you, so they have to be convenient.

Despite such convenient mobility, it was surprisingly uncommon for martial artists to ride horses.

This was because horses were unexpectedly high-maintenance creatures, and above all, they were very expensive.

A poor martial arts school disciple riding a horse was like an idiot riding around on a golden horse, just asking to be robbed.

And there was also the sad reason that after forming a bond, they could die or disappear.

In Zhongyuan, horse thieves were as common as bicycle thieves in Qing's hometown.

Moreover, once one became a Master, horses were not very convenient.

Since their own legs were sturdy, there was no need to borrow the legs of a beast. Furthermore, the feeling of riding while sitting on a horse's saddle was not particularly comfortable.

So, Qing had thought about wanting to ride a horse at least once, but she had never actually tried to.

Because Qing was faster than a horse.

Masters could all run faster than horses, but Qing didn't just stop there. She could continue running without getting tired.

Wasn't this the Qinggong that not even the best horses in the world could outrun?

Thus, the historic moment of riding a horse arrived!

"Oh. It's surprisingly not much, huh?"

"If you only have a sense of balance, riding a horse is not that difficult. The difficult part is controlling the horse freely."

"Hmm. Would that be difficult? Hey, Wang Goongdoong-ah, want to run a bit?"

At this, Daoist Pilmu hesitated.

"What did you just say?"

"Ah. His name is Wang Goongdoong. From behind, his ass looked as big as a door. Hey, let's go! Um. Won't you go? Would you mind going? Hey? Wang Goongdoong? You're not going to listen?"

Qing tried to poke the horse's side while tapping its belly as she had learned, but Wang Goongdoong just stubbornly kept to his slow, steady steps, saying 'You can poke all you want, I'm going to go my own way'.

What's this? Do I have the Triad Curse?

Why does every beast I come across decide to ignore me?

Whether it's that bitch Seol in the carriage or this guy, Wang Goongdoong.

Without any ulterior motives, and just as an unavoidable reflex, Pilmu, who had carefully observed the rear of Qing's saddle upon hearing the name Wang Goongdoong, was startled.

"It is dangerous."

"Huh? Dangerous? I don't think it would be dangerous to pick up the pace here?"

"That is not what I meant."

Horses were surprisingly muscular creatures, so even at their slowest pace, the walk, they could perform many movements.

They could turn, jump, lie down, or even quickly turn around 180 degrees.

So, surprisingly, many accidents occurred during the walk because a horse might suddenly get excited and perform an unexpected action, leading to a fall.

"Hmm. But it's not fast like this."

"It is originally a pack animal. It seems to be a particularly timid one, unwilling to leave the group."

"Hmm."

Qing recalled the long head that always turned back to look at her whenever the carriage moved ahead. It had a long face, probably because it was a horse.

Now that I think about it, it seems that it wasn't just asking me to take it out because it was smart, but rather it was asking for help with anxious eyes, saying, 'Awww, Owner, it feels strange, I'm tired, please take me out'.

Hmm. I thought it was a smart steed.

It was just a mutt.

Qing gently stroked Wang Goongdoong's mane.

Anyway, because of this unexpected horse riding lesson, their schedule had to be changed.

It was because of what she heard while learning how to take care of Wang Goongdoong.

Qing had thought that since it was a smart, docile, and affectionate animal, she could bring it to the Divine Maiden Sect and raise it. The disciples could ride it when they were bored, it could pull a plow in the fields, and it could pull a cart when they went out to buy supplies.

But after hearing about it, oh boy.

Horses were timid, making them more dangerous than fierce beasts.

A proper kick from their hind legs could instantly kill even a martial artist, and if they bit you, your limbs could dangle or even be severed.

If something was behind their butt, they could get startled and run wild, so they needed a stable to rest. But since horses were herd animals, they couldn't stand loneliness if left alone.

Moreover, they ate a lot and excreted a lot, so raising one was an immense amount of work.

It was a dangerous, picky, and labor-intensive animal.

So, what could she do?

They had no choice but to leave it at the Seolga Trading Company's stable.

Thus, on the tenth day, they arrived at Jagwihyeon!

"Thank you for the escort. Be safe on your return. Since our sect forbids men, I couldn't even offer you a cup of tea, even though you came all the way here. I'm sorry."

"It is alright. We will meet again."

Daoist Pilmu made a fist and palm salute.

Even though they were both Rising Stars, Daoist Pilmu maintained his politeness until the end.

He's quite a decent guy.

However, Pilmu's thoughts must also be considered.

During the Dragon and Phoenix Assembly, he had witnessed Qing's outburst, accusing the Daoist monks of not greeting their elders properly.

Not to mention, he had seen Daoist Changbin struggling in an ambiguous position, neither a friend nor a senior.

The coachman was from the Seolga Trading Company, and the carriage and one of the two horses belonged to the Seolga Trading Company as well. The other horse belonged to Qing, but they were all going back together anyway.

So, when they arrived at Jagwi, they were going to return it to the trading company and walk, but the coachman insisted that they didn't need to, begging them to let him take them to their destination as it was his lifelong wish.

Since he was so earnest about it, well…

Thus, clip-clopping along in the carriage, with Seol Yee-ri sweating profusely across from her, they finally reached their home, sweet home, Divine Maiden Peak.

"Stop!"

Just when the tall mountain path leading up to my house was right in front of me, right in front of the Divine Maiden Sect's gate, people appeared, blocking the disciples' return.

What? How dare they, right in front of Divine Maiden Peak's front yard! Don't they fear the Divine Maiden Sect?! Um, wait, huh?

Qing tilted her head.

Come to think of it, is Divine Maiden Peak's front yard really safe?

Back then, there were two formidable masters blocking this place, which was quite daunting at the time.

Of course, I'm confident I could take both their heads with one strike now, but back then, my realm was lower and I was older, right? Was it?

And didn't those Demonic Cult bastards kidnap someone right in front of here?

This time, there was a whole group of them!

Is Divine Maiden Peak's front yard really okay like this? 