\chapter{After The Fire (7)}

In their original state, martial artists who govern the energies within their bodies are extremely sensitive, delicate, and dangerous, to the point where even a slight touch can cause problems.

This was especially true after consuming elixirs.

Therefore, the act of someone nearby protecting them during such times is expressed as 'standing guard'.

Thus, Qing quietly left the guest room to stand guard in the yard.

Although Qing had just fed her, elixirs were originally not meant to be consumed carelessly.

Medical texts stated that poison could be used as medicine, which could be rephrased to say that medicine is essentially poison.

This was especially true for wild elixirs.

That was why martial artists did not consume elixirs raw but rather cooked them.

Cooked elixirs, refined into pills, were generally safe to consume without much concern.

Because they were made to be consumed that way.

When consumed in a healthy state, they were a fortuitous event that enhanced Inner Qi. When consumed in an injured state, they served as a panacea. This was why people's eyes turned red at the thought of acquiring such renowned pills.

Separately, it was said that consuming raw elixirs was better for enhancing Inner Qi alone, but who knew?

Did Zhuge tell her about this? Or was it Nanah? Anyway…

Plants that have absorbed the energy of a mountain for hundreds of years, or the inner core of a spiritual beast that has lived for hundreds of years.

The former, like a thousand-year-old wild ginseng, could be considered an elixir, but she couldn't quite understand what constituted the latter.

Surprisingly, in the world of Wulin, it was said that animals could occasionally awaken to martial arts.

Of course, they didn't separately govern external and internal energy like humans, but rather stored natural energy in some organ, drawing it out bit by bit.

Ah! The wonders of Zhongyuan' ecology!

Well, Qi was an all-purpose resource, after all.

It was a mysterious power that could turn people into superhumans, flying around and shooting laser beams in her homeland's terms.

In her homeland, there were things like danjeon breathing and Qi healing, but…

However, those were on the level of pseudoscience or the tricks of charlatans, such as mysterious metals that supposedly improved health and luck just by possessing them, the hexagonal structure of water, the theory that words have power, causing water to distort and plants to wither when cursed at, or attachments that blocked electromagnetic waves.

Therefore, this primitive, uncivilized ancient China was probably not the result of time-traveling to the past of the world she knew.

Then, what is it? A path not taken?

Perhaps a world where Qi was discovered and one where it wasn't, split apart, or maybe in the infinitely vast universe, there were twin planets that developed identically until they took a different turn.

At that, Qing looked up at the sky.

The unpolluted, clear night sky of Zhongyuan was filled with countless stars, flowing grandly.

Come to think of it, she hadn't really had a chance to look at the stars since her journey into Wulin began.

If it wasn't for that Celestial Martial Emperor or whatever forcing her to look at the stars, she might have forgotten about it altogether.

Qing easily found the brightest star and connected the prominent stars around it to form the shape of the Big Dipper.

The Big Dipper.

What was it called again? Ursa Major? Anyway, those Westerners, how can they see a bear in that, when it's clearly a dipper?

In fact, before her journey into Wulin, she was just a production worker who didn't have much time to look at the stars. So, the only constellations she knew were the Big Dipper and one that looked like the Latin letter W, um, but where is it?

Qing peered into the night sky, trying to find it, but other than its appearance, she knew nothing else. Moreover, there were so many bright stars that everything looked like it, making it impossible to figure out where it was.

Nevertheless, Qing did not stop searching.

But the more she looked at the night sky, the more unfamiliar it became.

Maybe, just maybe, as that old man said, there might be as many stars in this Zhongyuan sky as there are people.

As if I'm the only stranger in the entire world with different memories, as if I'm the only one in the whole universe.

That was why, from some point on, Qing stopped mentioning things she knew from her homeland.

From Western words to basic science, she erased all words and systems that people in this world wouldn't know.

Because, it's strange, you know?

What if they ask what that is?

What if they ask how I know?

I'm the only strange one, so I have to hide it well.

It was then.

Drrrk, the sound of a door sliding.

The expression of Qing, which had been forlorn and gloomy, instantly brightened, a welcoming smile blooming.

At this, Seol Ri hesitated, pausing with her foot halfway out the door, staring blankly at Qing's radiant beauty under the night sky.

It was unknown how long she would have stared if Qing hadn't spoken.

"Oh. How are you feeling? Does your energy feel like it's overflowing?"

"It's good. No."

"It's not overflowing?"

"Yes."

"Eh."

He was fed something good, but his response was underwhelming.

As Qing's expression turned sullen, Seol Ri tilted her eyebrows.

In the eyes of a skilled Seol Ri caretaker, that was a non-verbal expression of 'hmph'.

"I still need more."

"What? More? You want more elixirs?"

"No. Yes. No. I still lack much strength. To protect Young Lady Ximen, I need to gain more strength."

"Ooh."

It was a very commendable and touching sentiment.

She thought she lacked strength because she wanted to protect Qing, not because her energy was overflowing.

Has this child suddenly attained enlightenment after consuming the elixir?

She now even knew how to play with people's emotions.

"Your intentions are commendable. Haaah. What time is it already? I'm sleepy, let's sleep."

It was indeed late at night.

Judging by the position of the moon, it was past midnight. What, did it take two hours just to digest half an elixir?

She suddenly realized that this child was not just lacking in strength but lacking in many ways.

However, Seol Ri could be excused for this.

Inner Qi was relative.

If one already possessed ten portions of energy and absorbed one more, their dantian would already be capable of handling it, and moving ten portions of True Qi to accommodate one more wouldn't be difficult.

But Seol Ri had the Insignificant Arts, which meant she had pitifully little Inner Qi.

Surprisingly, it was comparable to a martial artist at the beginning stages of a First-Rate, but she had to accommodate roughly thirty times her capacity, considering she had absorbed one portion and had to accommodate about one relative to her existing energy.

Moreover, she had to convert an elixir that was well-balanced in Yin and Yang into one with extremely cold Yin Qi, which inevitably took time.

Fortunately, thanks to her previously emptied dantian, there was plenty of empty space, so at least that was a relief.

Therefore, Seol Ri had truly risked her life, not letting even a single strand of True Qi escape.

She had attempted to absorb beyond her capacity, risking Qi Deviation, which could shatter her dantian and twist her meridians.

But if she didn't say anything, Qing wouldn't know.

If she had known, she would have scolded her, asking what kind of idiot does such reckless things, and probably given her a nuclear noogie.

However, Seol Ri had no intention of speaking about it in the future, so Qing would likely remain unaware.

"So."

"Hmm? Why? Aren't you sleepy? It's normal to feel refreshed after absorbing an elixir."

"It's not that. Young Lady Ximen, why are you so nice to me?"

Seol Ri, who had no tact whatsoever, always had to voice whatever was on her mind.

For some reason, she stopped mid-sentence, hesitating, before firmly closing her mouth as if she had changed her mind.

"What is it? Why did you stop talking?"

"It's nothing. Yes."

What is it? Nothing.

Why did you stop talking? Yes.

Aside from the first answer, wasn't the second question usually asked to confirm something?

So, saying yes there? Yes? Is that right?

"You're making people angry, no. Nevermind."

Qing was an expert in raising Seol Ri.

This was just a stubborn person who was good for nothing, who, once she made up her mind, would never change it.

Since she had closed her mouth, no amount of prying would make her open it, so it was pointless to ask what she was going to say.

"Let's sleep. I'm sleepy."

"No."

"Oing?"

What is it?

"You don't want to? You're not going to sleep?"

"Yes. Right."

"Then what are you going to do?"

"Circulate my Qi."

She meant she was going to cultivate her Inner Qi.

Qing's eyes narrowed.

What's this? Now that she has a bit of Inner Qi, she's suddenly going to focus on cultivating it?

Without even sleeping at night?

There were always these types.

People who suddenly make grand resolutions, like deciding to lose weight from today.

Then they eat only one meal a day and start exercising, buying a year-long gym membership that will obviously go to waste.

Of course, there's no way that would work.

To achieve anything, one must start with small, weak steps, gradually getting used to it until it becomes a part of daily life.

Suddenly declaring, 'I'll show you, a completely changed me,' and going all out is a reckless and foolish act that's unlikely to last even three days.

"Don't do that, let's sleep at night."

"No."

"There's plenty of time during the day."

"I'll do it during the day too."

"You're going to circulate your Qi all day and all night?"

"Yes."

"Hmm. Why don't you… I can't sleep without someone next to me. Can't you sleep with me?"

"No."

Oing. What's with Seol Ri's attitude?

What's this, puberty? Is she rebelling?

"I'll be circulating my Qi next to you. Young Lady Ximen, you may sleep."

"But it's hot, you know. Now that your Inner Qi is abundant, can't you use your Insignificant Arts next to me to cool things down?"

"Abun. Dance."

At that, Seol Ri's gaze lowered and then slightly rose, but she didn't make eye contact. Instead, it went back down and then up again, shifting between the lower and middle, displaying a very rude attitude.

What's this? Where did she learn such bad manners?

As Qing was about to express her bewilderment, Seol Ri's response came a beat later.

"I can't."

Agh, seriously. She's so frustratingly stubborn!

It seemed like she was finally starting to get the hang of her cooling function, but suddenly there was an unexpected declaration of a strike.

What's this, betrayal? Is this betrayal?

Anyway, she was a useless one who wouldn't listen no matter what.

In the end, Qing just sighed deeply.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had nothing in particular to do at the Zhongnan Sect.

The transmission of the Ice and Snow Divine Palm was completed the next day, as Qing's martial arts learning was the epitome of effortless acquisition.

Reading the secret manual and demonstrating the movements once was the end of it.

The Martial Arts Window sparkled, and a purple border appeared.

But why, I wonder? Even though I obtained the Ice Dragon, I can't use it.

Now I can summon a majestic dragon from my right arm! But my dantian, my dantian…!

However, it wasn't something she could blame anyone for, and she couldn't exactly grind her teeth at the old man who had already ascended, or rather, passed away.

After that, it was embarrassing to just stay in someone else's house as a patient.

So, what else could she do? She had to go home.

"Why don't you rest and recuperate completely before leaving?"

"I've already delayed a lot of time, so I should return and pay my respects to my Master. It's not that far of a journey, anyway."

"I see. Resting at home is indeed much more comfortable."

Although Daoist Tajeong knew of Qing's condition, he didn't particularly try to dissuade her.

This was because the road from here to the Divine Maiden Sect was famously known to be very safe throughout the entire world.

To the south of Mount Zhongnan, the road stretching east to west was renowned as the safest route in the world.

There was no way it couldn't be safe.

Below, the vast mountain range surrounding the Sichuan Basin formed an impenetrable barrier that prevented people from coming and going.

At the far left end of the road was the territory of the Kongtong Sect, which reached Mount Kongtong, and as it entered Shaanxi Province, it became the domain of the Zhongnan Sect.

Further on, as it entered Hubei Province, the road led to Mount Wudang, the territory of the Wudang Sect.

And the Divine Maiden Sect was roughly within a stone's throw, as Zhongyuan' distance went, from the Wudang Sect.

Therefore, Tajeong could send Qing off without much worry, even though she couldn't use her Inner Qi.

Of course, that didn't mean the world of Wulin was a place where one could completely let their guard down.

That was why four mounted Zhongnan disciples were assigned to escort her, ensuring a safe journey home.

However, there was another problem.

"It's hot……."