\chapter{After The Fire (2)}

"Gramps, are you leaving already? Let's have lunch together."

"Weren't you planning to leave anyway? We can just meet again in
Zigui, so stop with the unfitting farewell."

Qing was planning to stop by the Zhongnan Sect after lunch and head
straight for Hubei, as it seemed that time had already been delayed.

On the way, she would stop by the Wudang Sect before going home.

Choi Leeong felt uncomfortable visiting the Zhongnan Sect due to his
past, so instead, he decided to take the young lady of the Jangheung
Trading Company to Nangnyeong.

What kind of people were those in Nangnyeong?

They were creatively vicious people who hung their father's corpse on
their shoulders and threw stones.

What kind of hardship they would endure when the enemy of the city
was thrown at them was unimaginable.

One certain fact was that it would be far more merciful to just kill her
now.

But why bother?

There was no reason to be merciful, so she would probably die in agony on her own.

Seol, now Seol Garyeon, said she had business in Seoan and would
return after finishing it.

"Hmm. Seol. Did you, by any chance, take a liking to crossdressing? Of
course, I believe hobbies should be respected. Yes. Since you've
become pretty, you might want to crossdress and all that."

Seol Garyeon's expression contorted.

"I have no such interest."

"Oh, really? But."

Qing pointed at Seol Garyeon's chest.

It was protruding, as if something had been stuffed inside.

With a woman's clothes and fake breasts stuffed in the chest, a gallant
beauty with strong lines was standing right there.

"Didn't you say you had business?"

"Well. What kind of business requires you to crossdress as a woman?"

"It's called a honey trap. When you're running a business, you
sometimes have to do some dirty work."

"I don't think you should reveal such a thing so proudly……"

Qing mumbled with a sour expression.

So, you're saying you're going to act all cute and charming in front of
a man in that outfit?

For the Seol, that is, the greatest intellect of Shaanxi Province, to do
such a thing… it wasn't exactly degrading since he looked good in it,
but still, um, what a waste of brains?

"So, you're going to act all cute and such? Can you show me?"

"A honey trap is about making the target beg and cling to you, you see?
If a woman acts cute and clings first, the man will soon get bored and
lose interest."

"Ah. A cold and haughty woman, I see?"

"I'm just imitating that."

Come to think of it, she had often left her seat, saying she had things
to do. So all this time, she was busy making a man's heart burn, huh?

How could I not have known about this fun thing until now!

We have to part ways after lunch!

How could you tell me such fun news only now!

Qing felt a great sense of betrayal.

"Why are you telling me this only now? If I had known, I would have
gone to watch."

"That's why I didn't tell you."

"You're proudly revealing it, but are you embarrassed?"

"It's not like that. However, if you were to show your face while I was
in the middle of executing my plan, wouldn't it all be for naught?
Especially with that one tagging along."

If two of the Six Flowers of Wulin were to tag along as spectators,
Seol Garyeon would transform from a handsome beauty into just a
handsome person.

Qing was convinced by that answer.

And then, something came to mind.

It was also something to ask a reliable intellectual.

"Ah. That's right. But like, I heard she couldn't learn that Ice
something Divine Arts?"

"Right. Her name was something like that."

Seol grinned bitterly.

"Those Ice Palace bitches are still at it. After calling her that, they
probably had a good laugh."

"What do you mean?"

"Well, think about it. Normally, they would just call her bitch or
something like that. But to give her such a name, to have her be called
like that… They must have had a good laugh after naming her."

"No, but seriously, how rotten do their personalities have to be to do
something like that?"

"Well, I wouldn't say they're particularly more rotten compared to
those in Zhongyuan. After all, aren't bastards treated worse
than servants here or there? They're just a bit more open about it."

"It sounds tremendous, though."

"It's not that different in Zhongyuan. Why don't you ask a
bastard from Zhongyuan later? However, if you're treated like
that here, you'd at least run away because you're disgusted."

"Hmm."

"In the Northern Sea, that's just suicide. Besides, how much food,
supplies, and dog sleds do you think it takes to get to the Central
Plains? So even if they're beaten out of boredom and treated like
servants, there's nowhere to run. That's all there is to it."

"That's quite vicious, isn't it?"

"Well. So be a bit nice to her."

"I couldn't be any nicer to her, you know?"

"It seemed like it."

Seol looked at Qing with a somewhat warm gaze and continued.

"So, you asked about the Divine Arts? It's probably because she's a
bastard."

"But she learned the Ice-White Palm Strike, didn't she? But why is she
being treated like that? What if she gets pissed off and spreads the
Divine Arts around Zhongyuan?"

"Let's say you're raising a dog. A mixed-breed without a pedigree. You
fed it, housed it, and clothed it, showing it great kindness. But then,
no matter how much you beat it or torment it, it just whimpers and wags
its tail. Would you even think that such a trivial dog could bite you?"

"But-"

"It's true that in the Northern Sea, even just feeding, clothing, and
housing is considered a kindness. So, bastards are meant to be used
and occasionally tormented for fun. If you take it for granted, you
won't even imagine that they could harm you."

And then, Seol grinned.

It was a sinister and ferocious, yet satisfied smile.

"To the extent that even when the disciples are dying one by one, they
would never think that a bastard was the culprit."

"So you're saying they're looking down on her like hell?"

"Exactly. And well. Even if she spread the Divine Arts, they can't learn
it anyway. It's not a martial art that can be learned just by wanting to
learn it. If you're not of the bloodline of the Northern Sea, if you don't
have the quality called Ice Crystal Affinity, you can't even begin to
learn it."

And that wasn't all.

Even if one could achieve such a thing, there was a limit to the level of
achievement that could be attained. For some, it was Three Stars, for
others, Five Stars, and for those capable of reaching Grand Star, it was
capped at Twelve Stars.

If one exceeded that limit, the Ice Crystal residing in the dantian could
not be controlled, and they would become frozen ice statues.

As such, even if one had the aptitude, they would teach a bastard,
regardless of their origin.

After all, aptitude was also about bloodlines.

It was a fight over how much of the blood of the founder of the
Northern Sea Ice Palace, the Ice God, was inherited.

Therefore, having Ice Crystal Affinity was proof of having inherited
the founder's blood, and they would be incorporated into the direct
line.

"But then? They're incorporated into the direct line. So why don't they
teach her the Divine Arts?"

"Well, that's what they say, but who would want a bastard as the
Palace Leader? My guess is it's one of two things, or maybe both.
Perhaps her aptitude was unexpectedly high, so they were wary of
her. If she was only going to reach Three Stars or so, they would have
just taught her."

"Is it? Is she? Talented?"

"Of course. I think so too."

"Then what?"

"It seems a talented child of the current Palace Leader has appeared.
The Palace Leader probably wants to pass the position to her own
child."

At that, Qing pondered for a moment.

"Then, what if… If I somehow learned the Ice-White Divine Arts, could
I teach it to her so she could learn the Ice-White Palm Strike?"

"I don't enjoy such pointless hypothetical games, but… If that were to
happen, I would be the one to ask you to do so."

"Hmm. I see?"

And then, Qing smiled mischievously and changed the subject.

"So, how's the honey trap going?"

"Surprisingly… Well."

"Is it okay to play with a man's pure heart like that?"

"He's the son of the Regional Inspector of Shaanxi Province. If you're
curious about what kind of person he is, go to the marketplace and
listen to the rumors."

That meant he was someone worth toying with.

Well, if Seol says so, then so be it.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

That Ice-White Palm Strike. When the dragon appeared, it looked so
cool. Mmm. I want it.

No, I must have it.

And it would also make the insignificant Seol a bit less insignificant,
which could be considered a win-win situation for both of us.

Of course, it wasn't because she felt sorry for her.

If one learns one, one more is added, making two Purple Martial Arts.
If this is missed and another martial art is exchanged, it would be two
against one.

That's half the profit, isn't it?

So, from a perspective of not being swayed by emotions and judging
with cool rationality, exchanging 4,000 Righteous Karma for the IceWhite Divine Arts was the right move.

It was truly being rational.

Thus, Qing casually brought up the topic.

"Hey. About that Ice-White Palm Strike. If I somehow managed to get
my hands on the Ice-White Divine Arts, could you teach me? We could
exchange with each other."

"No."

"Eh?"

Huh? A no was not within my expectations.

If she says no, then there's nothing that can be done……

Goodbye, my ice dragon. Although I couldn't have a black flame dragon
on my left arm, I thought I could at least have a blue-eyed ice dragon.

To the disappointed Qing, Seol surprisingly continued to speak.

And it was a rare, full sentence from her, who specialized in short
answers.

"Do you want to learn the Ice-White Palm Strike?"

"Yeah. It looked cool."

"If Young Lady Ximen wants, I will teach you."

"Oh? You'll teach me for free? Without the Ice-White Divine Arts?"

"Yes. Yes."

The no was not that no!

It was a no that meant she would teach her without needing the Ice White Divine Arts!

Huh? What is this? How thoughtful of her?

Well, I did take quite good care of her.

If you treat them well, they'll return the favor. Yeah, that's the joy of
raising a pet.

"But you don't have Ice Crystals. Even if you did, you wouldn't be able
to withstand the Ice Crystals."

"Then what about you? Even if I give you the text of the Ice-White
Divine Arts, if you don't have those Ice Crystals, you can't learn it
right away, can you?"

"No. I already have Ice Crystals in my dantian."

"Really? Then, whatever."

Just open your mouth and wait.

The Ice-White Divine Arts will come pouring in.

I'll stop by the Zhongnan Sect on the way.

"Ah. That's right. But are there any side effects with the Ice-White
Divine Arts or the Palm Strike? You know, like that Ice…Asura, where
the senses disappear with those types of ice arts?"

"No. No."

There are no side effects for Divine Arts or Palm Strike.

Ice arts dull the senses, yes.

Seol answered nonchalantly.

But in fact, this moment was a very historic scene.

Qing had actually asked about the side effects before learning
something!

It was truly a moment of evolution where a creature that merely
reacted to stimuli had advanced to the level of primates in an instant,
finally beginning to think.

However, her moment of thought was still short-lived.

After all, how could there be side effects to a Purple Border Divine Art?

If there were side effects, it would have been downgraded to Gold
instead of Purple.

Of course, there was the White Hand Demonic Arts, which became more
evil the more one used it, but as can be seen from the names of the
White Hand Demonic Arts' Movements, it was a demonic art created
with a very deliberate malevolence and resentment.

First Movement of the White Hand Demonic Arts, Absolute Rarity.

To take joy in the severing of lineage.

Unless a martial art was completely reinterpreted by someone at the
very end of the Transcendent Realm, it was bound to follow the original
Imagery it was created with.

As such, since the original Imagery of the White Hand Demonic Arts
was created with malice towards the world and viciousness, it was
inevitable that its owners could not escape from it.

At any rate, now that things were settled.

It was finally time to go see the Absolute Sword Wall again.

Fortunately, the Zhongnan Mountain was near Seoan.

After all, wasn't its name literally Zhongnan?

Originally, a mountain located to the south of a capital during a dynasty
was called Nanshan.

And since Seoan was once the center of Zhongyuan, the very
best among all the dynasties, it was the most legitimate of the Nanshan,
the Zhongnan Mountain.

Thus, if you just say Nanshan without the Zhong character, the people
of Zhongyuan would naturally think of Zhongnan Mountain.
Moreover, in the past, it was called Jungnanshan because it was a
mountain in the center of all under heaven, so Zhongnan Mountain
divided the northern and southern parts of Zhongyuan up and
down.

Therefore, after eating lunch in Seoan and slowly rolling along in a
carriage, one could reach the main mountain of the Zhongnan Sect,
Nugwandae, in just a little over two hours.