\chapter{After The Fire (4)}

Qing pondered over it.

Something was bothering her.

"Hey. Don't just stand there like a post, come sit here."

The Celestial Martial Emperor gestured with his chin, tapping the stone floor in front of him with the tip of his sword.

It was a new way of using Sword Force that Qing had never seen before.

"It's a stone floor. Usually, people ask to sit next to each other, right? And there's plenty of space on that rock over there."

"Are you trying to talk back to an elder? If I sit here, you should naturally prostrate yourself on the ground. Since you've got plenty of padding on your backside, it shouldn't be a problem. It looks plump and comfortable enough to sit anywhere."

"Is that really what's on your mind right now? Are you saying I want to hear such harassment?"

"I don't know. Maybe you're secretly dissatisfied with your current physique. So, are you going to keep standing? If you don't want to, then don't."

So, Qing obediently sat on the floor.

Ugh, it's a stone floor, seriously.

Qing lifted her butt slightly, supporting herself with one hand, and swept the ground with the other.

The White Hand Demonic Art, infused with True Qi, swept the stone floor clean, scattering pebbles and dust.

"Now. Look up there."

Then, the Celestial Martial Emperor pointed to the sky with his Sword Force.

As Qing tilted her head back to look up…

"Ooh."

The dark night sky was filled with stars, white, blue, red, and pale starlight densely gathered, flowing like a river.

It was the Milky Way, something she had only seen through screens back in her homeland.

The heavily edited photos that were practically works of fiction.

It might have been due to her superhuman eyesight, or the pristine air quality of ancient China where there was hardly any use of coal, let alone petroleum, due to the lack of development in petrochemicals, or perhaps because there were no artificial lights on this earth to illuminate the night.

Or maybe all three.

Because there was no light pollution, and with enhanced vision, she could see the sky clearly.

"The Milky Way."

To the people of Zhongyuan, the sky was inherently black.

In other words, the color of the sky was black to them.

This was because the first characters they learned were, 'Heaven, Earth, Black, and Yellow', which taught them that the sky was black and the earth was yellow.

Thus, while they referred to a clear sky as a 'clear sky with a bright sun' and a bright day as a 'bright day with a clear sun', the night was just a night.

They didn't use expressions like 'black sky', as there was no need to add the modifier 'black' to something that was inherently black.

Similarly, in Qing's homeland, they didn't refer to black people as 'black black people', did they?

"The Zhongnan bastards are obsessed with stars. The Thirty-Six Swords Under Heaven, Heavenly Star Sword, Limitless Sword, Galaxy's Falling Stars, Great Unity Divine Arts, Galaxy Heavenly River Divine Arts, Innate Arts, Big Dipper Divine Arts, Wandering Milky Way, Heavenly Dipper Big Dipper Formation. It's all stars, stars, stars."

"The names all sound cool, though."

"Tsk. Look at the sky again. Every person is born with a star. As there are countless heads in the world, so too are there stars above them."

"I heard there are a lot more stars, though."

"How would you know that? Have you counted? Have you counted how many people there are under this sky on this earth and how many stars there are above in that sky?"

"Well, no, but that's what I heard. Anyway, even according to you, we wouldn't know unless we counted, right? Whether the number of people and stars are the same."

"Tsk. So childish, always nitpicking. Are you a child? A child? A grown woman acting like a child. Not just grown, but overly so in all the wrong places."

Seriously. Wow. I'm at a loss for words.

Qing experienced a rare moment of being speechless.

Is this what the Greatest Under Heaven is? Did he win that title through arguments?

"Why argue with words when you have a good sword? Just stab them, and it's over."

"Can you please stop reading my thoughts?"

"Enough. If a person carries a star within them, it is called their Heavenly Star. A natural talent bestowed by the heavens, thus a destiny that descends from the heavens as starlight."

"Hmm. So in this universe, that's how it's considered. As if there are sounds and stuff."

"……? Why is the universe suddenly coming up?"

To the people of Zhongyuan, there was no concept of outer space yet.

There was only the idea of a higher realm for Daoists or the Three Thousand Worlds stacked vertically for Buddhists.

To them, 'universe' did not refer to the space outside the atmosphere, but rather 'cosmos' referred to fixed space, and 'universe' referred to flowing time, thus encompassing the entirety of time and space, the entire world.

"Never mind. But, you know, your star is a particularly ominous one among stars. Moreover, now is not the time for its orbit to be visible in this world. So, why did you take in that distant Heavenly Slaughtering Star? Why did you take such a distant star into your bosom?"

"Even if you ask me that… What does that even mean in the first place?"

"It means you're a complete bitch. Now. Tell me. You must have some idea, don't you?"

His way of speaking, seriously.

Qing just shrugged it off.

"Well. Actually. I keep hearing about qualifications. I don't know. I'm just… um. Just trying to, in a good way?"

"How? In what good way?"

"Is it fun to kill? It's so much fun to make them scream while pissing and shitting themselves? It never gets old? I want to do it again?"

"I came down here thinking maybe it wouldn't be so bad, but it's worse than I thought. Aren't you just a Great Demonic Adept yourself?"

"Just now, you said you came dow-"

The Celestial Martial Emperor cut off Qing's words.

"Yet your Righteous Karma is through the roof."

"Ah. You know about Righteous Karma too?"

Qing asked with a brightened expression.

What! So I'm not the only one who can see it!

Maybe I'm not so strange after all!

At this, the Celestial Martial Emperor wore a mocking smile.

"You're such a low-level trash that you don't know."

"I'm pretty much a Master, you know?"

"Since when was the Peak Realm considered a Master? You should at least reach the Unrestrained Realm to be considered barely beginning your journey. Once you transcend life and death, you can see it roughly. So, how did you manage to accumulate so much Righteous Karma with that level of yours?"

"That's because I only kill bad guys? Isn't it okay to kill those who deserve to die? It's actually beneficial to the world."

"No problem? Fine, I'll let that slide. So?"

"But then they all say the same thing. 'What gives you the right to judge?' It doesn't feel great. Honestly, I'm just doing good deeds while enjoying my hobby. What right do I have to declare divine punishment?"

"And?"

"That's it. Am I justified? Should I be doing this? Honestly, even a bad guy might not remain a bad guy until death. Of course, that's probably like one in a hundred, if even that."

"Considering such thoughts, you were awfully quick to kill without hesitation."

"Well, for one bad guy to change, a lot of good people have to suffer, right? Why should good people have to suffer just to reform a bad guy who deserves to die? Those people could be doing more good in that time."

"Hmm. I don't know where to start. Your thoughts are well-taken. You really sound like a bitch, it's driving me crazy. What a piece of trash."

Suddenly, more insults were hurled her way.

Qing made a sour face and grumbled.

"Why are you cursing again?"

"Aren't you asking me to take your side? So, are you saying you want to hear that killing is beneficial to the world, that you should kill without hesitation because the rising Righteous Karma shows that the heavens have permitted it, and that you are a human butcher? That's exactly what a bitch would say. You kill and then whine, 'I'm not in the wrong, am I? Please take my side.' What's that if not trash? You're absolute trash, aren't you?"

"Don't you think you should offer some comfort at a time like this? What if I become corrupt? What if I really become a Great Demonic Adept?"

The Celestial Martial Emperor snorted.

"Comfort, my ass. If you've chosen a path, don't seek understanding from others. And don't run from the consequences, take responsibility. That's what a martial artist is. Got it?"

"What if I really become a Great Demonic Adept? What if I go corrupt and start slaughtering everyone? Will you still say the same thing?"

"Then everyone in the world will try to stop you. Besides, you don't like being hated, do you?"

"Well……"

"And the Seventh Movement, Seeing the Moon and Forgetting the Fingers."

"Huh? Are we suddenly being taught a Movement?"

"Now. Watch carefully."

The Celestial Martial Emperor drew his sword and lightly swung it vertically once, then horizontally once.

"That's it?"

"That's it."

"You didn't even use Sword Force."

"Sword Force is starlight. But if you have seen the moon, you must forget the finger. Once you reach the self that the star points to, forget the starlight. Thus, if you no longer rely on the heavens, if you do not follow the mandate of heaven, if I am the center of all under heaven, if you fully look into and understand your heart, and if you establish the center of the world with my sword (Sword Establishes Zhongyuan), then the sword no longer needs to shine."

Qing looked back, then her mouth fell open.

A huge cross had been carved into the cliff.

Ten zhang vertically and ten zhang horizontally, it was a massive scar.

\textbf{Solitary Nine Swords, Seventh Movement.}

\textbf{Seeing the Moon and Forgetting the Fingers.}

"In the past, a Daoist was one who defied the will of heaven. Traveling against heaven, they wished to escape the lifespan set by heaven, to live long and healthy lives in eternal youth, enjoying wealth and glory, taking not one wife but three hundred and sixty concubines, and enjoying a different hole every day."

"Do you have to put it that way?"

"So that's how the very old Daoist methods were. Changing the course of life on earth to deceive the eyes of heaven with Formations, concocting elixirs by grinding up things that a person should never eat, and engaging in dual cultivation without creating offspring according to the natural order while accumulating Inner Qi through Health Techniques."

At some point, going against heaven started to be replaced with conforming to heaven. Since Jo Jung-yang solidified the laws of the Jin Sect, cultivating the Dao was altered to mean understanding the will of heaven and striving to become one with it.

"But a person should not do that. It is not about understanding and accepting one's natural disposition, but overcoming oneself so that the heart arises to move the heart as one wishes."

"Uh, wait a minute."

Suddenly, her mind became distant, the world blurred and smudged, and the stars in the sky drew long trails, forming a large circle.

"Fixed destiny is the star of heaven, the Heavenly Star. Inborn nature is destiny, so some say they lack talent, some say their nature is wicked, and some lament that their lineage is lowly, asking what can be done about being born this way. But are you going to just lament? Each person is the master of their own world, a change born to alter their own world."

The Celestial Martial Emperor stood up.

Although the tiny old man stood with his legs planted on the ground, at this moment, he was taller than anyone else, an existence larger than the world itself.

"Child born with the harshest nature, contemplate and struggle fiercely. When the time comes that you can move your heart as you wish, achieving self-reliance, then you will no longer be swayed by the starlight."

Amidst this, the Celestial Martial Emperor, radiating a brilliant human light, though unseen, seemed to be smiling.

Qing's body moved on its own, drawing the sword.

"Uh?"

"You should at least swing it once. Transcendent Realm? Your realm is so trashy that you'll be useless for a while. If you want to see other Absolute Sword Walls, rest for at least two months. Or you might actually die."

Now that he mentioned it, his smiling expression was full of a wicked, mischievous old man's slyness.

"Wait a minute……! Augh!"

Suddenly, her dantian churned, and all her Inner Qi surged, rushing through her meridians.

Although Qing's meridians were well-maintained with the effects of various Divine Arts, her Inner Qi was even stronger. 

As such, the bottleneck at the largest path connected to the dantian, the Jungwan, could not withstand it, causing an excruciating pain as if it was being torn apart.

And this pain spread throughout her entire body through the meridians. 

\textit{What the fuck is going on?! Why is my Inner Qi not listening to me……!}

Qing instinctively knew.

\textit{Ah. This. I'm fucked.}