\chapter{After The Fire (9)}

Qing quietly gripped the hilt of her sword.

Her condition was not yet good enough to use Inner Qi.

She was confident in fighting with her physical abilities, but only if her opponent was at a manageable level.

Even with just Sword Qi, if she tried to counter it without using any of her own, her sword would not last many exchanges.

However, she didn't need to hold out for long.

If there was a disturbance at the foot of the Divine Maiden Sect's mountain gate, her Master would soon arrive, riding on her sword.

But those Demonic Cult bastards must know that too, so… Hmm? Does that mean it's not a good idea to rely solely on my Master?

Qing signaled to Seol Ri-ri with her eyes.

Sensing the unusual situation, Seol Ri-ri, who had been sitting in meditation, exhaled a cloud of white, cold mist from her entire body.

It was a chilly aura that flowed from the Internal Energy. She had been diligently consuming elixirs, making her aura quite fierce.

At this level, she wouldn't get beaten up, so Qing felt relieved about that aspect.

-Aigo, good sir. What is the meaning of this?

-Who is inside?

-The disciple of the Divine Maiden Sect, Young Lady Ximen, is inside.

-Heuk heuk, is that so? A disciple of the Divine Maiden Sect…….

Qing quietly drew her sword.

At that, Seol Ri-ri suddenly opened a water bottle, poured it onto her hand, and with a creaking sound, a long, frozen sword took form.

What's that? Why does she keep showing off such cool things?

However, now was not the time for idle jokes, so Qing gestured with her fingers, signaling.

I'll take the left, you take the right.

Seol Ri-ri nodded.

And then, a voice came from outside the carriage.

-The Divine Maiden Sect is a forbidden place for men, is it not? I do not think you are a woman.

-I am only escorting her here and will return soon.

-Ah, I see. Everyone, disarm. She is a disciple of the Divine Maiden Sect.

"Huh."

What's going on? What's with this atmosphere?

Then, a knock came on the carriage door.

-Excuse me. You said you are a disciple of the Divine Maiden Sect, but we have orders to ensure that no men sneak in, so may we inspect the carriage?

The lowered voice was extremely polite.

"I was about to get off and head up to the mountain gate anyway."

Qing opened the carriage door and stepped out, where she saw a warrior in shining golden armor.

Since martial artists rarely wore armor, his attire alone indicated that he was a soldier of the government.

When their eyes met, he froze with an 'Uh, uh,' expression, staring at Qing without even blinking.

"Excuse me?"

"G-Gasp, my apologies, my apologies."

The warrior, whose ears were tinged red, hurriedly bowed.

He had been caught off guard by her gracious beauty without any mental preparation, so his heart pounded loudly, his limbs felt numb and shaky, and his voice naturally diminished, almost mumbling.

"Huh. What's going on?"

"Th-The Empress is currently holding a memorial service."

"Empress Dowager?"

The title Empress was reserved for the highest of superiors.

When Qing asked again, the warrior lowered his voice.

"Her Imperial Majesty, the Empress, has arrived."

The official title for an Empress was the same as for an Emperor, using the term 'Pyeha'.

"Ah."

So, that lady, huh?

Qing recalled the 'mother figure' she had met in front of the Shaolin.

Biologically speaking, she did seem to be her mother.

But Princess Yeonseol was Princess Yeonseol and Ximen Qing was Ximen Qing, so the more they were entangled, the more they saw each other, the more they would feel a sense of incongruity.

What was it again? The Ship of Theseus? What was it?

If the captain changes, is it still the same ship? Even if the captain changes, it's still the same ship, right? I don't think that's right. What if it's not the captain, but the owner that changes? If the owner changes the name, isn't it a different ship? What is it? I don't think that's it either.

Of course, who steers the ship or who the owner is doesn't really matter.

However, the truth was far away, and since Qing had no way of knowing, what could she do.

At any rate, Qing was not Princess Yeonseol, so the Empress would eventually realize that her daughter was gone forever.

However, she felt uneasy that it might end with a bitter conclusion of, 'You are not my daughter. Give me back my daughter, you monster'.

Thus, after climbing the steep mountain path of Divine Maiden Peak and finally reaching the entrance of the Divine Maiden Sect, located at about eighty percent of the mountain's height, the disciples on guard duty blossomed upon seeing Qing.

But that was it.

For some reason, they were standing guard properly, and only when Qing came close did they bow.

"Welcome back, Grand Elder Martial Aunt!"

"Welcome!"

Qing tilted her head.

Huh? Is this right?

Normally, they would have rushed out to greet her the moment they saw her face, chattering away with endless questions.

Since Qing's expression was quite honest, the disciples explained, giggling mischievously.

"There's a big guest here, so the Sect Leader gave us strict orders. She said to be prepared to get a bonk on the head if we acted frivolously."

"Ah. I see. A bonk on the head. That hurts……"

Qing quickly understood.

Under the nuclear head-bonk, all disciples were equal.

"Seriously, it hurts so much."

"She cried after getting hit once. Almost for a quarter of an hour."

"It wasn't a quarter of an hour, okay? I just, just shed a little tear, okay?"

"Is that what you call a little tear? Then if you really shed tears, the whole world would be submerged in water, huh?"

"What! Wanna go at it today? Wanna get your hair pulled out and really cry today?"

"If you cry, the world will be submerged in your tears, won't it? For the peace of the world, I shall endure today. Oh, but who is that next to you? Wow, so beautiful. I think I'm falling for her."

Whether it was because they were happy to see Qing or because the power of the nuclear head-bonk didn't reach the level that Qing was familiar with…

For some reason, these were the usual disciples of the Divine Maiden Sect.

I wonder if they're gonna get bonked on the head.

"This is Lady Seol I-ri of the North Sea Ice Palace. Seolhwa of the Five Martial Flowers, you know?"

"Wow! Seolhwa! The Five Martial Flowers!"

"Yes."

"Wow, her hair is so pretty!"

"Yes."

Seol I-ri responded to that.

"……?"

What's this? Is this how it usually goes? It was a look of bewilderment, wondering if this was the usual exchange.

Since they were the usual disciples and it was the usual Seol I-ri, it seemed there were no other notable events besides the arrival of the important guest.

Just then.

"You wenches. You can't even hold it in for this short amount of time before revealing your true colors. What a disgrace to have guests see such unseemly behavior."

"Eek."

"Eek."

The two disciples gasped in surprise.

Then, they creakily turned their heads like broken puppets, and upon discovering the Divine Maiden Sect's Sect Leader, Cheondungeom Wang Juhee, their shoulders hunched up tightly.

"S-Sect Leader. Since when have you been there?"

"Since 'Welcome back, Grand Elder Martial Aunt'. Why?"

It meant she had been watching from the very beginning.

Yet, no one, not even the perceptive Qing, had noticed her presence. It could be said that the mysterious Disappearing Steps of Wang Juhee, who was called the Cheondungeom because of her lack of presence, had deceived the world.

Of course, Wang Juhee hadn't used the Disappearing Steps.

Regardless, Qing, who had nothing to be guilty about, smiled brightly and greeted her.

"Sect Leader! This disciple has now returned."

"Yes. Was there anything of note? Let's see. This is Seol I-ri of the Ice Palace, right?"

"This insignificant martial artist, Seol I-ri, greets the Sect Leader."

Seol I-ri bowed politely.

Even Seol I-ri could not just reply with a yes or no to a senior of high status.

It makes me wonder if she's doing it on purpose at times like this.

"Yes. Yeonseo, guide Lady Seol here to the guest quarters. Qing, come see your Master right away."

"Yeeesssss~! Ouch! Ouch……."

SMACK! The playful Divine Maiden Sect disciple, Yeonseo, got a bonk on the head after all.

Since Wang Juhee was a disciple of Ximen Surin, she should be able to imitate a nuclear head-bonk to some extent.

After experiencing it, she couldn't resist the intense urge to spread this mysterious and profound enlightenment to others.

"Have Sarang guide her instead."

"Yes. Sect Leader. This disciple will obey your command."

After witnessing the nuclear strike, the Divine Maiden Sect disciple, Sarang, suddenly turned into a demure and modest lady.

This was the miraculous effect of Ximen Surin's nuclear launch educational method!

After such a long time… Or had it not been that long?

After all, she had only been gone for about two months, though she had usually been gone long enough for the seasons to change.

Anyway, upon seeing her disciple's face, Ximen Surin sighed deeply.

"Haaa. So. Princess Yeonseol, you say?"

"Ah. Did you hear about it already?"

"How could I not hear when I was suddenly appointed as a Royal Tutor overnight? I'm now suddenly a high-ranking official of the second rank."

The Royal Tutor was an official position within the Eastern Palace, equivalent to a very high-ranking official of the second rank.

For reference, the position was on par with the Provincial Governor, who was in charge of the administration of an entire province.

The Royal Tutor was responsible for the education of women directly related to the Imperial Family and was one of the few, and the highest, positions a woman could hold in Zhongyuan.

"Uh. Congratulations?"

BONK! It was a miniaturized version, a cute nuclear attack that could be classified as a tactical nuke, judging by the dainty sound it made.

However, the taste of the original's hand was more painful than the sound, so Qing rubbed her head until it was about to catch fire.

"To think I would ever hit a princess's head in my life. What a turbulent life I've lived."

"No, wait, why does this hurt so much……"

"You let your Protective Qi down, that's why it hurts. Why did you suddenly stop, after I had just taught you?"

"Well, that's, it's because this disciple has had some issues with her blood vessels-"

Before she could finish, Ximen Surin grabbed Qing's wrist.

Then, a warm True Qi flowed in.

"Ack! It hurts!"

With her torn-up blood vessels, the influx of True Qi was excruciatingly painful.

She had recovered a lot, so it didn't make her faint like when she first regained consciousness, but…

Seeing Qing's tearful eyes, Ximen Surin's expression became serious.

"What in the world is this? Why did a foolish girl suddenly become a cripple before returning?"

"It's not crippled. Well, this disciple saw the Absolute Sword Wall……"

Qing explained the whole story.

Ximen Surin's expression relaxed as if relieved.

"Hmm. The way I see it, upon reaching the Transcendent Realm, you seem to have a greater insight and realization. As such, the backlash has also become stronger compared to before. After seeing the first one, your arm became like that, and after the second one, all your blood vessels. If you see the next Absolute Sword Wall without properly recovering, you would die. Is that what they told you?"

"Yes."

"Haaa, nothing in life is ever easy, is it? Well, your realm is lacking, so what can you do. It seems best to refrain from seeking out the Absolute Sword Wall for the time being."

Her eyes narrowed.

"So, you said she was called Princess Yeonseol?"

"Uh. That seems to be the case."

"Did you know about it beforehand?"

"I only found out when I met the Empress Dowager. Um, to be honest, I don't really believe it, and I don't want to live as Princess Yeonseol either. This disciple would much rather be Ximen Qing, the External Disciple of the Divine Maiden Sect."

At that, Ximen Surin's expression softened.

It wasn't much of a surprise that the Empress suddenly came to offer a memorial service.

Since the Divine Maiden of Mount Wu, whom the Divine Maiden Sect worshipped, was known for her romance with the Crown Prince of old, a tale of the connection between a celestial woman in heaven and a terrestrial prince, it was rare but not unheard of for women of the Imperial Family to come and offer a memorial service.

However, she was completely caught off guard when the Empress suddenly bowed deeply and greeted her as Great Teacher.

Great Teacher? Was Her Imperial Majesty the Empress saying she would renounce the world and enter the Daoist path?

It was a moment that truly made her eyes go dark!

Fortunately, that wasn't what the Empress meant by joining the Divine Maiden Sect.

It was also common courtesy in Zhongyuan to address a child's teacher as Great Teacher.

Then, she wondered if perhaps… Could it be that her disciple had been hiding her identity and snuck in?

Of course, it was unlikely, especially since she had picked her up herself, and the appearance of a dirt-covered mole like her was not something a princess would do.

Still, she had to confirm.

And at this moment, hearing from her own lips that she wished to live as Ximen Qing rather than as a princess, Ximen Surin felt a sudden release of tension, her mind becoming dizzy and her heart racing, as an indescribable sense of relief washed over her.

And at the same time, a great realization struck her.

Was this child so precious to me?

At first, she had taken her in because she admired her righteous spirit as a woman and her outstanding talent. She believed she would represent women all under the Heavens and bring a new wave for all females in this world.

But how did she come to cherish her so?

Was she so worried and anxious about losing her?

Thus, Ximen Surin's face bloomed into a smile.

At this, Qing tilted her head.

She suddenly seems to be in a very good mood.

Then, with a satisfied expression that she hadn't shown in a long time, she spoke.

"Did you say it would take about two months to recover? Coincidentally, Her Majesty said she wished to hold a three-month memorial service, so the remaining time would be about that. You will attend to her during that time."

Qing made a face of disgust.

"Me? But, I, well. Honestly, I don't even remember, and she says I'm her daughter, but I just find it awkward. What if she eventually can't find her previous daughter's appearance and asks who I am, demanding her daughter back? What do I do then?"

"Don't say such absurd things. Even if you have no memories, she is still your mother. And even if you have no memories, people have a way of unconsciously showing things, so how could she, as your mother, not recognize that?"

But that's the problem…….

Qing's expression was quite reluctant, so Ximen Surin gently stroked her disciple's head.

"Even if you decide to live as Ximen Qing, should you turn away from a mother looking for her child? When else would Her Majesty come out like this? It's only two months out of your long life, so serve her with respect." 