\chapter{After The Fire (1)}

In Qing's subjective opinion, Nam Munhae, the young lady of the Jangheung Merchant Guild, was a bitch who deserved to die.

Everyone in the land of Naknyeong would think the same, and if the people of Zhongyuan knew the truth, they would not hesitate to spit on her.

This was because the primitive, ancient, and uncivilized Zhongyuan was not such a hospitable land to live in. As such, there were no idiots who spouted bullshit like 'life is precious' due to some retarded moral pretense.

However, even a bitch who deserved to die a hundred deaths, or rather, a bitch who deserved to die three thousand deaths since a hundred was far too little, was still a precious daughter to Nam Munseongsam.

Even if she was a sinner, what must it be like for a father to have to hand over his own child?

Moreover, since he was handing her over to his enemies, it was terrifying to even imagine how horrific her end would be.

However, Nam Munseongsam was a giant who had built the most prominent merchant guild of an entire province.

If any other old man would have simply lain in bed and lamented to the heavens, he instead sought a solution rather than collapsing helplessly.

Thus, Nam Munseongsam, who had gathered his three sons, spoke.

"We must get Hae-ah back. We must get her back. Which of you will go?"

"Father? Please calm down. Tell us slowly. Where are you saying we should go?"

"Where else! We must go to Naknyeong!"

Nam Munseongsam shouted abruptly.

"We must go and bow our heads to the ground, begging for forgiveness. And spread gold. Aren't they all just beggars whose property has been swept away by the flood, anyway? Yes. Go and slip thirty taels to the magistrate of Naknyeong and make sure the sheriff is well-taken care of as well."

"What you are saying is…"

"I have said this many times before, but even public sentiment can be bought with money. Go and give ten gold pieces per head to anyone who says their family has died. Even if they had lived, they would never have earned ten gold pieces in their lifetime, so the remaining ones will snicker and laugh, saying it was good that they exploded and died. If their family is still intact, they will probably just lick their lips, wishing they hadn't died."

If Qing had heard this, she would have been dumbfounded.

If only he had done this earlier, when Qing was working hard as a carpenter and a female physician, such a comforting shower of money would have rained down on them.

Then, Qing wouldn't have needed to cause all this chaos, lighting a great fire that would gradually spread in the hearts of the common people of Zhongyuan.

But he had no intention of doing so from the beginning, so it was inevitable in a way.

However, even if his response was delayed, Nam Munseongsam's gold treatment would still be effective.

Therefore, time was of the essence.

Nam Munhae, his precious daughter, had to be saved before she fell into the hands of those vile beggars and suffered a terrible fate.

"It is fine to spend any amount of gold. Go now and spread the wealth. And that bitch…"

A thick hatred formed in Nam Munseongsam's eyes.

"Yes, they say she is a Great Hero of the Orthodox Faction, so she is too noble to be touched, is that it?"

Originally, the Jangheung Guild had very strong and skilled ronin as retainers.

Wasn't even one of the Five Great Ronin, the Nine-Sectioned Whip Ronin, a part of them?

However, since that Nine-Sectioned Whip Ronin had betrayed them and left, taking his ronin juniors with him and saying that a new Hidden Dragon and the disciple of the Zenith Among Women might come, he had also taken his own daughter and left.

How could he dare to face an opponent that even the Nine-Sectioned Whip Ronin avoided?

So the other ronin also gradually found excuses to leave, saying it was time for them to go.

Moreover, there was no time to ask for help from the government, much less the sects of Seogan that had always sucked up their protection fees, so the empty house was overrun by the masses.

"Even if it costs me my entire fortune, I will not let that bitch go. If… If the Orthodox Faction cannot touch her, then we can ask those from the Unorthodox Faction. Yes, who will go?"

"Father? Where are you saying to go aga…"

"To the Four Evils! Go and tell them. If they kill the Heavenly Flower Sword, I will give them a thousand taels of gold!"

Previously, the bounty on Un Yeonyoung (Ximen Qing) was ten thousand taels, so a thousand taels seemed a bit too little.

However, it had to be taken into account that 90\% of such bounties were scams. Furthermore, considering that illegal items (including people or what used to be people) were used to generate astronomical profits compared to the original cost throughout the entire Zhongyuan, the Jangheung Merchant Guild, which was only the best in one province, was a bit of a harsh comparison.

"There is no time to waste like this. Who knows when Hae-ah will go to Naknyeong. How much gold do we have now? We must prepare immediately!"

Then, Nam Munseongsam jumped up and ran out the door.

The three remaining sons looked at each other.

Then, the third son, who had just become the youngest, spoke up.

"Brothers? We need to talk. Are you going to spread gold? Has that old man lost his mind? Why should we care about that bitch? Has he forgotten how he used to treat us?"

The guild's assets were mostly in the form of credit transactions left in promissory notes, so the available liquid assets were barely enough to be spread around Naknyeong.

If ten gold pieces were given to each family head, that's one tael per person. Even excluding cases where entire families were wiped out, leaving no one to receive compensation, it would easily cost over a thousand taels.

On top of that, the Provincial Governor would have to use his influence to portray the embezzlement of flood relief supplies as an unfortunate natural disaster caused by heavy rain. As such, they had to show their sincerity to the officials of Hanam Province.

And there was a bounty of another thousand taels?

"If we do this, we'll all end up as beggars. Besides, if that bitch comes back safely, she'll just take her place as the successor and boss us around again. That old man always favored her, saying she's the only child for him. I can't stand that sight anymore."

The remaining two looked at the third son.

They had never had a good relationship, treating each other like enemies since birth.

But at this moment, there was a deep understanding and connection between them that could be felt just by exchanging glances.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Today, the talk of the town in Seongan was, of course, about the great victory achieved by the most brilliant star of Wulin's rising stars and the Greatest Beauty Under the Heavens, the Heavenly Flower Sword Great Hero Ximen Qing, together with ten thousand of the masses.

Of course, the masses didn't number ten thousand, not even a thousand by a long shot.

However, heroic tales were originally like this, inflating themselves beyond objective facts for their own glorification.

This was not a lie, but rather a natural instinct for all humans, regardless of East or West, past, present, or future.

As such, the Heavenly Flower Sword had to be a Great Hero.

The protagonist who led this great victory had to be great for each person who had shared in this historic moment to have their own face and status elevated.

Thus, Great Hero Ximen Qing was the greatest intellect among martial artists.

Also, she was a peerless beauty, not just the greatest under the heavens, but the greatest of all time, so beautiful that even Xi Shi would bow her head in shame.

And she was a celestial maiden who had descended to earth to care for the common people.

Truly the greatest among the common people, and because she was a woman, she was the most beautiful lone flower among them all.

The first to bloom red among the common people.

The Red Flower, the Supreme Red Among the Common People. The Red Flower…

A Red Flower is too fragile, is it not? The Great Hero has the bearing of an imposing ruler.

Then, the Crimson? Yes, the Crimson Flower!

In an instant, everyone felt a thrilling electrifying sensation!

What was this feeling?!

Although they did not know what it was, it was the starting point of a new title spreading among the people, enthusiastically supported by the masses.

The Crimson Flower Heavenly Maiden, Ximen Qing!

And there were those who shed tears, showing an unusual level of emotion at this.

When the Great and Noble Supreme moves, even the arrogant people of the capital bow their heads and follow like loyal dogs!

Truly the brilliant light of our lives!

The most noble Sun itself!

A Crimson Flower is not a flower, but a fire.

The red fire, the sacred Holy Fire, shall blaze in the human world. Verily, the Crimson Flame Stands Alone.

When that time comes, the whole world will finally realize who their true master is.

With that, Her authority shall unite the world as one. The Holy Fire is One. The Crimson Flame is One!

The loyalty of the cultists grew rapidly.

It had already reached a level close to madness through brainwashing that had continued from their youth, but now it could be said to be madness itself.

If the command of the one they admired was more precious than their own lives, then it was only right to call them mad.

Thus, Qing's name was elevated and prepared to soar to the heavens.

And the power of the common people, the power of our customers, the power to reclaim our rights, declaring that we are the masters because we feed the merchants, began to spread like wildfire.

And the wind that would further ignite this fire was the news that spread the very next day.

The lord of the Jangheung Merchant Guild had collapsed!

It was said that he had suffered a stroke, twisting his limbs and contorting his face, rendering him a cripple unable to speak properly.

Truly, the wrath of heaven had descended.

Otherwise, how could such a healthy old man suddenly become disabled overnight?

Of course, there were exactly three people in the world who held a different perspective.

"Father, your lifeline is truly long. How could you endure after consuming such potent poison without dying instantly? Hmm. Was it because you took it with the tonic? What was it? A hundred-year-old wild ginseng from Goryeo? It seems the medicine was indeed effective."

"Well, the poison that Big Brother prepared did have quite a strong smell. It wouldn't have been noticed if mixed with a tonic. And since it was a tonic, that old man probably just gulped it down in one go, thinking it was good for his body."

"Isn't this better? If he lives long like this, we might even hear people call us filial sons. Don't you agree?"

Nam Munseongsam's heart was torn to shreds upon hearing those words.

Though he had collapsed, unable to do anything except blink his eyes and faintly tremble the ring finger of his left hand, with all his nerves damaged, his consciousness remained.

He was trapped in a body that had been poisoned and was now paralyzed.

This is why the ginseng of Goryeo is known to be the best among the three, with its efficacy being the greatest! It's practically living proof.

"Father, even if you can't hear us, don't be too upset. Do you remember? When I was young, I once threw a coin to a beggar. You slapped me then. You asked if I didn't know how precious money was. You told me that a man born as the son of a merchant had no right to be so soft, and that I had to be ruthless. I still remember that time vividly. So I became ruthless. Why would you squander such precious money just to save that bitch Hae-ah?"

"Exactly. That old man used to say with every breath that we should be the ones taking, not being taken from, and that those who are taken from are fools. So what now? Are we supposed to let our share be taken just to save that promiscuous bitch? Are we supposed to be fools? No, are we not your sons just like that daughter of yours? I have so many things I'm upset about."

"It's all the old man's fault anyway, so don't be too upset. Do you know? I've never felt any brotherly love in my life. After all, wasn't that old man the same, backstabbing his own brothers to get to where he is now? Do you think we ever considered that sly bitch our sister?"

Then, the second son laughed.

"Ah. But now I finally understand what brotherly love is. Since the Jangheung Merchant Guild is done for, let's split it three ways and help each other out like brothers."

"Honestly, he always favored the eldest or the youngest. What about me and the second brother? I've always felt like an afterthought. At least he arranged a solid marriage for the second brother. Am I even his son?"

"Solid, my ass. Do you have any idea how much I'm suffering, stuck with that shrew who looks like a rotten potato? Damn, because she's the daughter of the Provincial Governor, I can't even have a single concubine."

"Then, Second Brother can take over the brothels and gisaeng houses. Isn't it like having fun with women as your job?"

"You, Third, wow, why didn't I realize how smart you are sooner? Yes, I'll take the gisaeng houses. Since our father is down, let's have a drink together as brothers for the first time. After getting drunk, it will all be an act of filial piety. Eldest, will you join us?"

"Ahem. You think I was comfortable being the eldest? Fine, from now on, let's forget about competition and be partners. Let's let go of all the hard feelings from the past."

It was the moment when brotherly love, something that had never existed between the three brothers before, finally sprouted in their hearts.

After all, they had never been brothers in their lives, merely competitors fighting each other according to Nam Munseongsam's inheritance score sheet.

But now, there was no need for that.

Nam Munseongsam's heart was wretched and horrified as he watched his sons happily marching out together.

His parenting had not only failed but was also so remarkable that it deserved admiration.

Three of his children were scoundrels who had poisoned their own father for money, and one was an infamous villain who had killed three thousand people.

You bastards, do you think you will be safe?!

You will also face divine punishment!

You will face divine punishment!

And at this very moment, Nam Munseongsam finally called out to the heavens.

As a cripple who could only move a single finger.