\chapter{After The Fire (6)}

Qing knew of the famous elixirs of the world.

At this, the elder burst into laughter.

"Originally, the Dao of the Jin Sect teaches to distance oneself from vain dreams. What is the art of crafting elixirs? Is it not just a vain sound, seeking immortality? Even after receiving the teachings of Grandmaster Chongyang, the Mount Hua bastards who insisted on alchemy were truly wicked."

However, Mount Hua was already closer to being a large sect than just a Daoist order, so it was not particularly strange for a large sect to research elixirs.

"Besides, don't they have a lot of good herbs there?"

Mount Hua was renowned for its treacherous terrain, considered one of the most perilous mountains in Zhongyuan.

The meaning of a treacherous mountain was that there were many places untouched by human hands, where rare and exotic herbs grew in abundance.

Compared to that, Zhongnan Mountain, famous for its beautiful scenery, was a scenic spot in Shaanxi.

As a result, there was hardly a place where the footsteps of people had not reached, making it a desolate mountain where even a small wild ginseng root was hard to find.

"So, we bought a few and stored them."

"Can you give me such a precious thing?"

"This one is not that precious."

"Yes?"

"Open it."

Qing then opened the wooden box, and for some reason, it was filled with finely crushed pieces.

"While examining how it was made, it ended up being about half."

"Ah. Yes……"

Qing has obtained a Zixiao Pellet (half)!

Since it was what remained after being examined for research, the originally well-rounded pill was somewhat misshapen, and the color was also off…….

Still, gratitude was gratitude.

Even if it was only half, it was still a renowned elixir of the world.

But then again, was it okay to just dissect and study the elixirs of another sect?

Of course, Qing did not hesitate to ask about it since she never held back from voicing her curiosities.

"What's the difference between us and the Mount Hua Sect? If there's something good, we share it. In the first place, Mount Hua originated from our Zhongnan, so I guess you could say that Mount Hua's elixirs also originated from us."

If the disciples of Mount Hua heard this, they would have been furious.

"That way, you can accept it without worrying, and we can give it without feeling burdened. The Sect Leader was considerate in that regard."

Originally, elixirs were a matter of life and death.

If a perfectly fine elixir was given, only for there to be a shortage later on, leading to an unfortunate event, one could not help but feel resentment.

So, just take the half that's left.

In fact, Qing sharing her insight of the Absolute Sword Wall was the price she had to pay, considering that the Absolute Sword Wall was a legacy left to Zhongnan.

Thus, with something given and something received, Qing did not owe Zhongnan, nor did Zhongnan owe Qing.

Giving a whole elixir on top of that would have been a burden, but a half-eaten elixir could be accepted without feeling indebted.

Of course, Qing regarded elixirs as something great, but roughly in the same way one regarded pills.

She would be grateful for half and grateful for a whole pill, but it wasn't to the extent that she would feel burdened by the thought of having to repay such a favor.

This was a case of overestimating Qing.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The inside of Qing's dantian was bustling, with all her True Qi gathered for a rare occasion.

This was because the outside, meaning beyond the dantian, was utterly destroyed, making it impossible for them to go out.

Demonic Qis huddled in a corner, trembling, while Blissful True Qi glanced at the Yue Maiden True Qi.

However, the Yue Maiden True Qi shook her head, signaling to just leave them be. As such, the Blissful True Qi could only smack its lips and glare.

Just you wait and see. You're all on thin ice.

The Demonic Qis sighed in relief, but since there was nowhere else to go in a dantian dominated by Buddhist and Daoist energies, they just huddled in a corner, exchanging sad glances as they lamented their pitiful existence.

Right then…

Kukuku……! went the laughter of the Heaven-Shattering Demonic Qi.

The Demonic Qis, already feeling miserable, rushed over to beat, scratch, and trample on the Heaven-Shattering Demonic Qi, venting their frustration.

Today, the Heaven-Shattering Demonic Qi was beaten again.

Keuheuk, keuk! Keuheuheuk, heuk, keuke……!

Yet, the Heaven-Shattering Demonic Qi was still laughing…….

Amidst all this…

At this time, when all paths in and out were utterly destroyed, the door to the dantian suddenly burst open.

Who's this all of a sudden? A new family member?

The Daoist and Buddhist True Qi turned their heads in unison, and the Demonic Qis, which had been beating up the Heaven-Shattering Demonic Qi, paused in their assault and looked on with anticipation, wondering if it was a new big sister.

The Heaven-Shattering Demonic Qi just kept going, Keuk, keuheuk, heuk.

However, the new family member was unfamiliar.

It wore a thick, white, fluffy animal hide and entered expressionlessly, looking around before heading to one side.

Then, it took out a huge iceberg from somewhere and planted it firmly on the floor of the dantian.

At this, the three sisters of Ice, the Jade Maiden True Qi, Ice River Demonic Qi, and the Cold Qi, rushed over with bright faces.

Wow! Ice Essence! It's so. COLD.

There's nothing better for Yin-Cold energy. I just wish I could explain it better……

Around the Ice Essence, white frost rapidly spread across the floor of the dantian.

However, when the Yue Maiden True Qi lightly stomped her foot, a line was drawn exactly halfway, preventing the cold from crossing over.

On the other side, the Zhu Yang True Qi, looking displeased, ignited the other half into a sea of flames.

Thus, half was frozen and half was burning.

The Heaven-Shattering Demonic Qi, caught exactly in the middle between the two, was half cold and half hot, but since it was just laughing, the exact sentiment was unknown.

At any rate, it was at this moment that a new member, the Ice White True Qi, settled into the dantian.

Ximen Qing, Ice White Divine Art, the most cost-effective Six Stars.

"Hoooooo."

Qing came out of the state of having her brain roughly handled and let out a deep breath.

The Status Window's method of engraving knowledge was something she could never get used to.

This feeling of having her brain violated was indescribable, leaving her feeling lethargic and constantly dirty for a while.

As Qing grimaced at the lingering discomfort…

Creak, the door opened, and Seol Lee entered.

"Ah. Right. Hey, Hole. Come here. I have an amazing story to tell you."

"First, have your medicine. And I don't like being called Hole."

Seol Lee approached, carrying a large tray with a large bowl filled to the brim with a generous amount of herbal medicine.

However, her hands trembled as she moved the tray, and the movement was so slow that it seemed time was flowing ten times slower, making it seem like the medicine would never arrive.

Qing just stared blankly, wondering what was going on with her, until the bowl finally came within reach after a long while.

Ah. The medicine is filled to the very top, huh.

Even in a large bowl, the medicine was filled to the point of almost overflowing.

So Seol Lee was moving like a snail, ten times slower than usual, trying not to spill even a single drop.

But seriously, from where did she even start to bring it at this speed?

Unlike the trembling Seol Lee, who was clearly struggling with just a bowl of medicine, Qing's sense of balance was unparalleled.

She lifted the bowl and brought it to her mouth, gulping down the vitality-boosting herbal medicine with a hearty movement of her throat.

"Whew, that's really fucking bitter."

Still, knowing that the medicine was bitter, they had neatly piled up expensive rock candy on the tray.

Qing quickly grabbed one and put it in her mouth, then offered another to Seol Lee, who obediently opened her mouth and ate it.

"Now, Hole, sit down here. I have an amazing story to tell you."

"I don't like being called Ho-"

"You don't like it, right? Then, Hole, sit here. I have an amazing story to tell you."

"I don't like being called Hole either."

"So demanding. Lee-ya. Here, no, why do I have to say the same thing so many times? Sit or stand, whatever. \textit{'A while ago, in the North Sea, which is even further than the North Sea, I saw a frozen wall that stretched transparently to the abyss. There was a cave of barbarian orcs nearby, uncivilized, dirty, and ugly, who ate raw meat. When I asked, they said it was ice over ten thousand years old and revered it as sacred. Their insignificant language is not worth translating, so I'll just use the most superior language to call it Ice White. Ice White Divine Art.'}"

She didn't know who the founder of the Ice White Divine Art was, but it was clear that they had a severe case of racism.

To think they would call themselves barbarians of the North Sea.

And to think they would say that the language of Zhongyuan was not theirs.

"Young Lady Ximen? Now-"

"Whatever. I'll recite the formula, so open your ears and listen carefully, okay? Hole? Earhole? Hole for ears?"

"You keep… It's too much."

"Anyway. \textit{'I was deeply moved by the Ice White, so ice, coldness is the strongest force in the three thousand worlds, freezing even space and time, the universe itself. Thus………'}"

As the formula began to flow, Seol Lee quickly closed her eyes and focused her ears.

Qing recited the same formula two, three, four times. And just as she was about to recite it for the fifth time…

Suddenly, a fierce north wind blew inside the room, dropping the temperature of the late summer to that of deep winter.

Hmm. It's refreshing.

If there was a downside to the Ice White Divine Arts, it was that one became insensitive to cold but more sensitive to heat.

This was different from the Invulnerability to Heat and Cold that martial artists developed as they became Masters.

Invulnerability to Heat and Cold only meant that one's health wouldn't be harmed by heat or cold. It didn't mean one wouldn't feel hot or cold.

It just meant one could go, 'Ah, it's so fucking cold,' or 'Ah, it's so fucking hot,' and move on. It didn't actually block heat or cold.

So, this characteristic of the Ice White Divine Arts was actually a function, not a side effect.

Because after all, the North Sea was only cold, so it was all beneficial with no heat to worry about.

But Qing was hot.

She thought she could just use the Cold Heart Arts to cool down, but when she tried, the Cold Heart Arts had stalled after she had suffered a blow to her Inner Qi.

This was a characteristic of people who were impulsive in their actions without much thought, always ending up paying the price.

It could also be said that Qing was a master of inefficiency, having no thoughts but an urge to do everything immediately, often doing the same work multiple times.

Anyways, thanks to that, it's refreshing.

As the icy wind blew through the room, a familiar and nostalgic feeling surged.

It felt just like being at the top of the Divine Maiden Sect, in her cramped, uncomfortable, cold room where snowstorms blew right through, rather than just drafts.

Hmm. Thinking about it, I want to go home…….

How long had it been?

Seol Lee suddenly opened her eyes.

Then, with eyes that had changed to a slightly softer shape, she looked at Qing.

Qing took a piece of rock candy and popped it into her mouth, then reached out again.

Seol Lee licked it and her eyes widened.

Even though she usually didn't show much expression, when she was surprised, her eyes would widen. Hmm, she's cute.

"Uwup."

"Haaah. Don't spit it out, you can't. It's medicine, you know? It's called a Zixiao Pellet. It's precious, so swallow it and circulate your energy."

Qing bragged, even though she had received it for free.

It was the remaining fragments of half a Zixiao Pellet given by the elder, which she had clumped together into a smaller pill.

Qing, after all, had never been short of Inner Qi after reaching her realm.

Rather, she had too much, which was the problem. She had even been thoroughly taken advantage of by that old man, the Celestial Martial Emperor.

Moreover, Qing had the Supreme Healing Pill.

She felt it would be a bit of a waste to feed even that to someone who was utterly useless and incompetent.

But half a Zixiao Pellet seemed like it would be just right, as the elder had said.

Now, our Hole has changed. I can look forward to her becoming a cool hot pack……

Huh? Wait, what the hell?

Come to think of it, I took her with me because I thought she'd make a good hot pack, but wasn't she completely useless at that simple task until now?

I've been feeding her, clothing her, bathing her, putting her to sleep, and putting in so much effort, but she hasn't been able to do anything as a hot pack.

But now it's time to get something back.

Why was it, 'You will be paid'? Where did I see that?

Anyways…

With that Divine Art and half an elixir, shouldn't she at least be half as useful as half a person?

I'm not even expecting a full person's worth, you know? 