\chapter{After The Fire (3)}

The Zhongnan Sect! (Mount Zhongnan Sect)

When it came to the Zhongnan Sect, it was the head and sacred ground of the largest branch of Daoism, the Quanzhen School.

In the distant past, there was a Daoist named Wang Zhe, also known as Wang Chongyang, who had tried to enter government service when he was young but failed the civil service examination.

Thinking that he might not be cut out for academic pursuits, he tried to learn martial arts to make a name for himself. However, he failed at that as well.

Perhaps the shock of failing both the civil and military paths was too much for him, because he suddenly set fire to his residence and wandered the world, acting like a madman.

(If you think about a Westerner who failed to change his career and burned down the world instead of his house, one could say that Wang Chongyang was rather moderate in comparison.)

However, if a historical text mentioned 'acting like a madman', it usually meant not a lunatic but a beggar. In other words, he burned down his house and became a beggar, but it was embellished to sound more impressive by saying he feigned madness.

Then, he met a master and attained great enlightenment. This master was none other than one of the Eight Immortals, the Sword Immortal Lu Dongbin.

At any rate, this was how Wang Chongyang achieved great enlightenment, took in disciples, and finally established a foundation on Mount Zhongnan. It was the moment the Daoist branch Quanzhen and the Daoist sect Zhongnan were born.

It is worth noting that one of Wang Chongyang's disciples, He Datong, established a Daoist temple near his master and spread the Dao. This temple would become the Mount Hua Sect.

Thus, the greatest achievement of the Zhongnan Sect was that it spawned the Mount Hua Sect.

The only shortcoming of the Zhongnan Sect would be that it always lacked Masters compared to the Mount Hua Sect. To put it bluntly, they were always far behind in terms of skill.

The Zhongnan Sect could also feel aggrieved.

The Mount Hua Sect openly called itself the Mount Hua Sword Sect, and was closer to a secular sect than a Daoist temple.

Moreover, the martial arts of Mount Hua were deadly, focusing on killing the enemy, making them very practical and realistic arts of murder.

Furthermore, the Mount Hua Sect concealed the cruel killing intent of their martial arts with flamboyance.

So even ordinary people who knew nothing about martial arts would go, "Wow, Mount Hua Sect! Wow, Plum Blossom Sword! But wait, weren't there only a few plum trees on Mount Hua? Hmm, whatever!"

However, the Zhongnan Sect was an orthodox Daoist sect among orthodox Daoist sects.

Of course, this claim was also pushed by the Qingcheng and Kunlun Sects.

As a result, the characteristic of being an orthodox Daoist sect was shared by the three sects, making their distinctions somewhat faint.

However, the Zhongnan Sect was not particularly concerned about this.

Because they were much wealthier than the Mount Hua Sect.

The biggest characteristic of an orthodox Daoist sect could be said to be its wealth, after all.

When it came to martial arts, the Mount Hua Sect might be more renowned.

But if one were to hold a ritual at a Daoist temple and had to choose between Mount Hua and Mount Zhongnan, wouldn't they naturally head to Mount Zhongnan, one of the three great sacred sites of Daoism?

Moreover, due to a long-standing custom, if a member of the Imperial Family visited to perform a rite, it was considered natural to pay for it with the surrounding land. And the Zhongnan Sect was the top choice among the imperial descendants among the Daoist temples of Zhongyuan.

Of course, it was still not comparable to the Buddhist sacred sites of Mount Song and Mount Emei.

At any rate, for these reasons, the Zhongnan Sect was very rich in land.

The land of the Zhongnan Sect even stretched to the front yard of the Mount Hua Sect!

As a result, a strange situation had arisen where people were paying protection fees to the Mount Hua Sect while farming the land of the Zhongnan Sect.

Thus, the scenery of the Zhongnan Sect was splendid.

Well-built temples were laid out neatly and orderly over a vast area, almost like the downtown area of a city.

As Qing passed through the gates of Zhongnan with Seol Lee-Ri in tow, the vast temples of Zhongnan, built on land that had been flattened by the application of countless amounts of gold and silver, stretched out in a grid-like pattern reminiscent of the planned cities in Qing's hometown.

After registering their names on the visitor's list and resting for a while in the guest hall, they soon received a message to come up and present their greetings to the Sect Leader.

Upon entering the Sect Leader's Hall, a middle-aged man wearing a Daoist robe that glittered brilliantly, as if it were painted with gold or made of pure gold, greeted Qing warmly.

He was the Sect Leader of the Zhongnan Sect, Daoist Tajung.

"Little Sister Ximen greets the Sect Leader. How have you been?"

"I am Seol Lee-Ri of the Ice Palace. Greetings."

"Oh. If it isn't the youngest. Yes. And is this the child from the Ice Palace? I've never seen you before. Or have I? Anyway, welcome. Did you have any trouble on your way here?"

"No. The Abbot of Shaolin asked me to convey his regards."

"What regards would a Daoist have for a monk? So, did you gain any insight from seeing the Absolute Sword Wall of Shaolin?"

"Yes. I am ashamed to say, but a little."

"Oh. Good, good. So, which number was it?"

"Excuse me?"

"Ah, no, that's not it. Could you perhaps tell me which Movement it was?"

"Ah. The First Movement. It was the Movement called Solely I Prevail."

"Hmm."

Daoist Tajung made a sound of regret.

Honestly, the martial arts of Zhongnan were not particularly powerful in actual combat.

Of course, that's compared to the Divine Arts of the Nine Sects One Union.

If Qing had listed the martial arts of the Zhongnan Sect, she would have seen a dazzling display of radiant gold.

At any rate, having already acknowledged that their martial arts were somewhat lacking compared to other members of the Nine Sects One Union, they had been secretly hoping for the First Movement after hearing about the Nine Swords of Solitude.

Wouldn't the First Movement be connected to the most fundamental, basic, and original essence of the martial art?

But Shaolin, of all things…

To think that they would eat the Ninth Movement and claim to be the best under the heavens, yet come down to the First Movement to secure their position. How shameless.

"Then, we have the First Movement and the Eighth Movement."

"Yes. That is correct."

"Hmm. I will not be greedy for the Ninth Movement. But perhaps, what do you think about the Seventh Movement? After all, the Zhongnan Sect also has a deep connection with the number seven."

"Uh…… I do not decide that."

"Hmm. That is true."

Daoist Tajung's shoulders slumped.

"Well. Let's see, ugh, what time is it, ugh, it is a bit early for dinner. Let us first prepare a splendid meal, and then we can have dinner together after seeing the Absolute Sword Wall."

Wearing a golden Daoist robe and silk clothes, he drawled his words with a cheerful rhythm, looking more like the owner of a wealthy estate than a Daoist.

However, his words pierced through the listener's heart and resonated with their very soul, proving that he was indeed a True Daoist, even with his appearance.

"Hehe. Thank you."

"No need for thanks. Well then. Shall we go?"

And so, Qing rose from her seat.

But then…

"Um, Great Sect Leader. Aren't there quite a lot of people coming along?"

"Honestly, shall I tell you the truth? Or should I tell you the even more honest truth?"

"If it's all the same, both?"

"Honestly, if you happen to enter a state of trance and perform a Movement like during the martial arts competition, everyone wants to see. And if we're lucky, maybe one of our disciples will gain some enlightenment."

"And the even more honest truth?"

"Daoists are people with nothing to do. Would they read boring Daoist scriptures instead of watching a pretty beauty? Or perform unresponsive rituals? They're all bored out of their minds, so there's no reason for me to stop them."

His words alone made him sound like a heretical cult leader with his bizarre speech.

In fact, with the golden adornments on his head and the silk clothes, his appearance alone was enough to make him seem unfit to be a Daoist.

However, unlike his speech and appearance, his Righteous Karma count was truly authentic.

In fact, the Zhongnan Sect had so much money that they didn't know the value of gold and silver and just used it carelessly.

And when Daoists have gold and silver to spend, what else would they spend it on?

So they fed the hungry, clothed the naked, and housed the homeless.

The terrain of Mount Zhongnan was beautiful but not rugged. Therefore, it was easy to take a light stroll through the mountains while chatting with fellow martial artists, and they soon arrived at the Absolute Sword Wall.

And as soon as they saw the Absolute Sword Wall, the Insight of the Celestial Martial Emperor stirred and Qing's mind was lifted.

The world turned gray.

At Mount Hua, she had seen the Celestial Martial Emperor perform a Movement, and at the Shaolin Monastery, she had personally experienced his strike.

And this time, it seemed to be an observation rather than an experience.

In a world that had lost its color, an old man with a stubborn impression sat cross-legged on a protruding rock, standing out with his vivid colors.

The Celestial Martial Emperor just sat there with a sullen expression, his chin resting on his hand, looking in Qing's direction.

What is it this time?

Qing waited for the Celestial Martial Emperor to do something, her heart pounding. It would have been nice to have some snacks, though. Maybe I should bring some corn or something next time.

But the old man did nothing.

About an incense's time passed, and he was still just sitting there, breathing quietly, showing no signs of doing anything.

"Huh. What's going on? Why is he just sitting there?"

Then, right on cue, a monologue flowed out.

"I'm waiting."

"Oh. It seems he's about to start now."

"……"

"……"

But again, there was only silence.

Qing tilted her head.

What? Do I have to wait for something too?

After about another incense's time…

The Celestial Martial Emperor finally opened his mouth again.

"What a tenacious bitch."

It was an abrupt curse.

"What a rude bitch."

And another curse.

Just as Qing was starting to feel that something was off…

"How long do you intend to just stand there blankly? Shouldn't you greet an elder first when you see them? You're not properly brought up, are you? Being rude is one thing, but that reflects poorly on your parents. Huh?"

Qing looked behind her.

There was nothing but a gray world and a gray stone wall.

"Um, are you perhaps talking to me…?"

"Then who else would I be talking to?"

"Uh. Are you able to see me?"

"What, do I look like a blind old man to you?"

"No, that's not what I meant. Um. Alive? No, that's a bit weird. I came to see the Movements left on the Absolute Sword Wall, and you didn't do this at other times, so?"

"Ah. I see. Is that so? Was that what that bastard left behind? Now I understand. You won't get it, but you'll understand eventually. There's no need to try to understand until then. Yes, anyway. Let's stop here with this conversation."

For some reason, a huge surge of anger welled up inside Qing at that moment.

What's with his way of speaking? Why is he suddenly getting on my nerves?

At this, the Celestial Martial Emperor chuckled.

"It's a joke. When I talk like this, everyone thinks there's something more to it and they cling to me, asking what it is. So? How is the main body? Did the real Celestial Martial Emperor die?"

"They say he has ascended."

"Did he finally do it? I knew he would."

"Then, you're not the Celestial Martial Emperor himself?"

"Of course not. How should I put this? The Secret Manual he left behind? The Sword Essence? The Sword Heart, they say. You saw it and it evoked an interpretation, or something like that."

"Sword Heart?"

"You'll be able to do it too when you become a Master of my level. Of course, that day will never come. Not everyone can become a Master, you know."

"Even if I become a Master, I don't think I'll be able to do this. Isn't this like magic or Daoist arts?"

"It's not that grand. Why? When you read the writings of sages, don't you sometimes deeply empathize and understand their inner meaning? If you look closely at my Sword Marks, you'll come to understand my great will, that's all."

Somehow, the imagined figure was very different from what she had expected.

She had imagined a more serious, stubborn, and, well.

A profound old man.

"Well, that's because that's the kind of Celestial Martial Emperor you imagined. After all, people see the world through their own eyes, so the me you interpreted is like this. But what's with the records that I look like this? Isn't this just some ill-mannered thug?"

"Huh. You think so too?"

"Yes."

Well, the Celestial Martial Emperor that Qing had heard of was someone who caused a ruckus at the Imperial Palace, a ruckus in the Demonic Cult, a ruckus with the Unorthodox Faction, and even a ruckus with the Blood Cult. He was basically just chaos itself.

"Hmm. I did it for the good of the world. To call it just causing a ruckus. How upsetting."

"Huh. You can even read other people's thoughts?"

"Well, it's the Celestial Martial Emperor you created, after all."

"Hmm. I don't know. Can't you just show me the Movements and get it over with?"

"No."

"Why not?"

"Because you're marked by the Heavenly Slaughtering Star. Right now, you're on the verge of Demonic Deviation with just one wrong step. You'd become a Demonic Human. And not just any Demonic Human, but a Great Demonic Human at that. A Great Demonic Human marked by the Heavenly Slaughtering Star. How dreadful."

"Great Demonic Human. The wording sounds a bit off."

"Would it sound good to have 'Great' attached to a Demonic Human? Not only are you rude, but you're also stupid, huh."

"No, why are you being like this? Can't you speak more nicely?"

At this, the Celestial Martial Emperor made an expression as if he was truly dumbfounded.

"I told you, it's because of you. You must want to be cursed at. Why, I wonder? What's the problem? What's bothering you?"