\chapter{Karma Comes Tumbling Down (1)}

Qing sees the world through her skin.

If there were any creatures with similar abilities, it would not be wrong to say that they were bug-like.

In any case, this ability to read space through atmospheric flow expands as the area of ​​skin exposed to air increases.

Since it's not about understanding the movement of fluids, but rather a collection of experiences accumulated unconsciously, the more familiar a space is, and the more strongly the experience remains in the unconscious, the clearer it becomes.

What if someone suddenly appears and whispers in your ear?

Something suddenly appeared behind me, clinging to me, without any sign of presence, as if it had skipped the process of approaching.

Naturally, it comes with that much fear.

That was the reason why the blue was frozen solid.

How? What kind of ghost was this…?

"Oh my, why are you so stiff?"

"Uh, uh, there was some misunderstanding, I did impersonate a bit, but, uh, so let's say it was something we mutually agreed upon, so I think Nyenyeong will understand too……"

"Oh my? You know me? Hmm, who are you?"

"omg."

Only then does Qing realize who the owner of that soft, familiar voice is.

Miss, the ultimate boss has arrived.

What was it, why did it suddenly appear?

Suddenly, the starlight blades that filled the cabin and countless swords of strong energy flashed through Qing's mind.

If you open this, you'll die!

Strong and weak, Qing immediately transformed into a water lily.

"That, that, uh, I'm sorry……."

"Oh my, how you're so shrunken. How cute. When you do that, even I feel weak. Okay. Did I do something wrong, or not?"

"I was wrong……"

Then, an elegant chuckle came out.

It was a moment when Qing saw a glimmer of hope.

"however."

A sticky, beautiful voice, like the sound of evil itself if expressed in a voice.

"Why did you do it when you knew it was wrong?"

"Huh."

"Then that won't work, right?"

"Oh, sorry, sorry……"

"If you're going to feel sorry, shouldn't you never have done it in the first place? Tell me. Why did you do it?"

"I'm sorry, ugh."

Qing gasps for air as something tingling touches the back of his neck.

"I already heard you apologize? I was just curious. Why did you do that?"

"Ugh, I guess it just popped out because I was in a hurry. It's not like I have any ill feelings towards them. It just kind of fell into my throat, and without me knowing it…"

"Hmm……."

Hot breath keeps seeping into my ear.

Unable to turn his head, his frozen blue eyes rolled around.

"You mean earlier? That thing you told me about called the Divine Power…?"

Qing saw hope again.

This guy also wants to use the magic of absorption!

"Hehe. If you want, I can tell you. I'll tell you. I'll call you right away, huh."

The force that keeps pressing into the back of my neck.

Qing immediately shut her mouth.

"What's that really strange, mysterious martial art called? Oh, right. The Unmarried Art. It's called the Unmarried Art. Oh, by any chance, do you know what that cute, sexy art is?"

Qing's eyes darkened.

Miss, I've been caught.

"Hehe, that, it's called the Tangseontal duty."

"Oh my. What a remarkable feat."

"Uh, if you want-"

"Okay. Then let's do it like this."

"Uh, how was it?"

Then again, there was a loud, hearty laugh.

"Okay. I'll show off that awesome new skill to everyone fighting here. I'm sure everyone will be thrilled. Would you accept it without exception, all of you great swordsmen here? What do you think?"

It was a sound that gave me goosebumps just hearing it.

"Um, was there any other way…?"

"Of course. There are other ways. In there, oh my, aren't there some faces I recognize? Joohee and Geomchi Orabuni? There were some I didn't know, though."

Qing's heart sank.

In an instant, I stumble, my legs give out, I sway, I lean forward without realizing it, and sweat drips down my entire body.

No way. No way.

"No, that's not true. It's no fun if we start touching it now, right?"

Is this what it feels like to be dragged out of the abyss?

Qing was relieved for a moment.

The only thing that remains was the sound of my heart beating wildly, pounding against my chest.

"So, you super-brained, beautiful girl, hehe, you decide? Hand over four of your friends, and I'll let you go. Or would you rather please give everyone here pleasure with that body of yours? Okay. I'll count to three, so you have to decide. Otherwise, you'll have to do both, right? One."

"I will! I will, so please……"

"Oh my. It's already fun. But… you have to remember, I told you all here. If there are some who won't cooperate, you'll have to force them to cooperate."

Qing nods his head endlessly like a crazy person.

"Hey. You might die, right? Does it sting for a second? Sting."

And then a sharp pain in the back of my neck.

Qing came to his senses.

No, no. Come to your senses.

Even if the sky falls, there was a corner to rise from. I don't know how a safe zone can exist when the sky falls, but let's think, let's think.

There must be a way, a way.

Qing desperately searches for a way.

You can do as you are told.

I could, but I doubt this horrible bitch would let me off easy just because I told her to.

I said it was all about peeling, peeling, and spraying, right?

It was a premonition close to intuition.

Qing's head was spinning like that.

Rolling it?

Suddenly, a sigh of relief, "Haaah," brushed past his ear, and a cautious hand wrapped around Qing's waist.

"Oh my. My goodness. Miss Ximen. I'm surprised. I knew you were still alive somewhere. But to show up like this? How mischievous."

"Huh."

"Somehow, the way you look so hunched over was so cute, doesn't it remind you of me? That's why I decided to give you a light punishment."

Qing realized that even though it was the same voice, the feeling of listening could be so different.

Unlike before, when his voice was sticky and full of malice, his soft and gentle voice clearly contained affection, a kindness that could be called affection.

While I was holding onto her waist, I felt Unyeon-yeong bury her face into the nape of my neck.

Qing was initially greatly relieved.

This? Do you think they'll let this slide?

"Hey, Miss Un?"

"Oh my, what do you mean, Miss? Didn't you just call me 'Nyong'? Hehe, that's right. Miss Ximen was right. How could I blame you? A super-brained, beautiful girl. How embarrassing. But I like it."

"Hey, girl? If you let me go now-"

"No."

A firm rejection comes flying in.

"Oh, so you want me to stay like this?"

"No. You should be punished."

"You just said you wouldn't blame me."

"You can't be so quick to speak like this. Really. If you're Ximen, you can sell my name around like crazy, right? But."

But? Qing gulped.

"You've been hiding your identity and acting so arrogantly, Miss Ximen. If your identity were revealed, wouldn't you feel so embarrassed you'd want to die? Oh, just thinking about it makes me laugh. How can I possibly endure this?"

"Can't you please bear with it……"

"No. I like the kind of Miss Ximen who's always confident, and sometimes acts like a mean bitch, but still sharpens her sword inside. You can't hide your true identity like that, can you? You should be confident, Miss Ximen, and even if you're cowardly, you should still be Miss Ximen. You can be mean, but not cowardly. I don't like the cowardly Miss Ximen."

"Then I won't do it again-"

"Oh my? Are you saying things you don't mean? You're going to do that in the future, aren't you?"

Miss, this isn't working.

It's so spooky, it's a ghost.

Qing-i stuck out her tongue.

"And Miss Ximen. I have children of my own to protect, too. Just like you, Miss Ximen, are trying to protect your friends. So, it's difficult for me to just let this go."

"then?"

"So, I have no choice. Miss Ximen, you'll have to endure a bit of hardship, right?"

"Can I hear what kind of trouble you're going through?"

"Like this?"

Thud. In an instant, the sound of feet stomping was loud.

It felt like my body was floating, and I was flying through the air, looking down on everyone from a high place.

Qing glanced down and saw a strange coffin standing on top of it.

"Everyone? Everyone, could you please stop fighting for a moment? You have to listen to me."

A gentle voice.

But for some reason, everyone stopped and looked up at me.

A chill runs down Qing's spine again.

Now that I think about it, I was held for quite a while.

How could there not be a single interruption after so much time spent being held from behind?

As if no one could see me and I was in a different space.

"You bastard! You super brainless, beautiful girl!"

Jun Ki-chung shouted as he saw the woman behind him and the man who suddenly appeared.

Those inside didn't find anything strange.

However, the unmanned personnel outside looked at Jun Ki-chung with eyes full of suspicion.

A super-brained, beautiful girl? Is that it? A nickname? Is that the taste of the ultimate eccentric?

Junki-chung's face suddenly turned red, and he gritted his teeth and glared at Qing.

"You bastard, Yun Yuanying, I won't forgive you……."

Qing was being treated unfairly.

No, why are you blaming me?

Then, just like that, the sound of snapping fingers straightens out the chaotic atmosphere.

"Okay. Everyone? I'm Yun Yuanying, former undercover patrolman for the Wulin Alliance, head of the Jinju Unga family, and currently a member of the Blood Cult."

"Carnivore!" "Carnivore!"

Yun Yuanying tilts her head at him.

"Oh, come to think of it, there was another impersonator? Who could he be?"

"Haha. Right. I'm curious about that too."

Qing awkwardly clapped his hands.

Yun Yuanying lets out a sweet sound, saying, "Hmm," but then decides not to care.

"And the person who was being held here, who dared to use my name, I want to let you know that you have made a great misunderstanding about me."

The martial artists inside the cave immediately understood.

What kind of crazy woman in the world would say such nonsense as being a super brainless beauty or the strongest woman?

And then he looked up at Qing with cold eyes, so even though he was looking up, it felt like he was looking down on him.

It was a look filled with deep regret.

It was a look in my eyes that made me want to scream at him to stop looking at me like that without me knowing.

"And this person was also the master of the Absorbing Magic? He planned to cause discord among you all, pit you against each other, and then sneak away alone."

The unmanned personnel outside also looked up at Qing with cold expressions.

Likewise, the gaze seemed to be looking down, this time with deep contempt.

"Well, everyone? Aren't you curious about this person's identity? Who on earth was this woman wearing a human face mask?"

"That's right!" "Take that mask off now!" "Who the hell was that vile bitch?" "Reveal it! Reveal it!"

Then, petitions started popping up.

Qing was sweating profusely.

"Oh, hey, girl? Didn't you say it was a bit difficult, a bit difficult? Suddenly, the atmosphere was so public that-"

"fizzle."

As Yun Yuanying's hand stroked the back of his neck, Qing closed his mouth again and became silent.

The hand that had been gently stroking the smooth nape of Inpimyeon-gu's neck for a while now snaked downwards and gently stroked the tightly wrapped cotton cloth.

"Hey, girl? Ugh, sexual harassment was a bit much. Oh, wait, that's…! This was crossing the line-"

Then, draw a circle with your finger in front of a somewhat hard part.

At that moment, Qing's body jumped up in surprise and he flinched.

"Easy. Are you hurt?"

"yes."

The fingers slide under the chin.

And then, quietly, it will rise upwards, and the pressure that has been squeezing your chest will disappear and follow you.

"Hey, wait, wait!"

"It would be a shame to hide something so wonderful."

The people gathered in the room felt as if they had heard something like that.

Of course, it couldn't be helped, as I witnessed the miraculous sight of a heavy mass of flesh suddenly filling up the once flat chest and rising up to fill the space.

A great sense of liberation and relief washed over me as the pressure bandage was removed from my chest, but at the same time, I was drenched in cold sweat.

Because the fingers that had cut off the chest cover were now gently rubbing the bottom of the cotton pad between the collarbones.

"Hello? Hey, this isn't real. Didn't you say it was a bit difficult? A bit means a little, or a little bit, or a little bit? Seriously. Hey, hey, hey! Please, please!"

Qing's words become urgent.

As if a blade was attached to my finger, a cool sense of liberation came rushing up to my Adam's apple as it sliced ​​through the leather of the human face.

The air was finally flowing, and my skin, which was swollen with sweat, was finally breathing, saying it will live, but I am not in a position to feel that refreshment right now.

"Can't you really spare me just this once? If I keep doing this, I really can't live? Will I die? Will I die of shame? Will I die? Will Ximen-cheong die?"

In fact, it was Qing who did the shameful thing in the first place.

How shameless was this to just go out and use someone else's name?

Suddenly, the news of what happened in Yun Yuanying flashed through my mind, and when the rumor spread throughout the martial arts world, Master, you guys, our disciples of the Shinnyeomun, the elders of Meng, and everyone at Seolga Sanghoe…

Qing's eyes darkened.

\textit{No, absolutely not. I'd rather die. How on earth can I walk around with my head held high?}

This was the way of Karma.

Don't they say you reap what you sow?


\vfill
\begin{lstlisting}
	The chapter title is a reference to Studio Ghibli's film, 'Memories Come Tumbling Down'
\end{lstlisting}
