\chapter{Karma Comes Tumbling Down (14)}

\textit{Three Transcendent Realm Masters who don't match up.}

\textit{Yeah, it's better than just one-on-one.}

Qing lightly shook off the tension.

In fact, it could be said that Qing's fighting style was to win by packaging it nicely.

Making surprise attacks out of the blue, luring them into letting their guard down with a beautiful appearance, blurring their minds with nonsense, and when dealing with multiple people, digging in and using them as a shield, etc.

What if it's not packaged nicely?

He's just a dirty, deadly brawler.

But now it's a fair fight.

The thoughts of the unmanned personnel or onlookers may be a little different, but at least that was the case for Qing.

Even though it was done with the help of military force?

Even so, it's only for filtering out the rabble. What use was an army of a thousand men against those who are determined to die, even if you die too?

If they fight close together anyway, the military was useless, and the iron soldiers on the watchtower are just decorations, so it would be impossible to fire arrows in the first place on a platform filled with onlookers.

From the beginning, it's a fight between masters who change their positions in a variety of ways.

When you shoot an iron oar, you know who you're going to hit.

In Zhongyuan, there was the Hu clan, in the Western Regions, the Tel clan, in the hometown of Qing, the Go clan, and in the fictional character, the Le clan, it was a possible art for a new courtier.

Besides, although the Qing originally used a wide battlefield, the duel arena cannot be said to be that large.

If you wag your tongue in front of these people, rumors will spread throughout Zhongyuan that the Cheonhwa Sword's mouth was so dirty it's like a cesspool.

So, to this extent, it can be said that it's a very fair match.

Qing looked at the three avengers with her sword hung down.

Then, the tallest swordsman among them opened his mouth.

"I am Oh Soon-hyun's Danhwacheol, and my younger brother was Danhwarak. He was a fierce-looking young man of thirty-three, with dark skin, thick lips, and a slightly small right eye. Do you remember him?"

\textit{Aiss, somehow bread comes to mind.}

But Qing held back.

That's not something you should say in front of people.

So she asked back instead.

"Was he a righteous man?"

Danhwa-cheol smiles brightly at him.

"No. But it's enough reason to make a life-or-death match with you."

"Okay."

Qing looks at those who remain.

One swordsman, one spearman holding a single spear.

The remaining people also each talk about their own relationships.

A swordsman who seeks revenge on his enemies.

And Chang-soo, who wants to avenge his disciple.

And then silence.

The avengers, approaching slowly step by step, stop outside the agreement.

An attitude that's extremely cautious.

I'm absolutely not underestimating the Qing, so if we leave things as they are, the standoff will continue forever.

Qing sighed and took a deep breath.

The most important thing for Qi was breathing.

When you inhale and your lungs are full, you feel energetic, alert and sharp, but on the other hand, when you exhale and your lungs are empty, you tend to be vulnerable.

So this was a kind of provocation.

The moment Qing completely exhaled and the exhalation turned into inhalation, they would all rush in and begin their attack.

Qing begins to breathe in slowly, then exhale slowly again.

And then, as Qing's chest pain gradually subsided, the moment came when he finally exhaled all the air he had!

"You barbarian bastard! What are you doing!"

A voice suddenly rings out loud.

Even the pronunciation was slurred and the tone of speech was familiar from hearing it over and over again. It was the fat Povidone Jang So-nam of Cheonhao-rang.

"I said it myself! I won't forgive anyone who pushes me away without a parent! You little piglet, you're just like a pig! I remember the feel of the scaffolding on my back!"

The strange cries of the monster following behind.

The skinniest guy in the room kept reaching out and surprising the fattest guy.

Bloody hand shadows that fill the space in an instant, such as belly fat and breast fat.

"Great man! That's a secret great man!"

"What a monster! He was a master of the martial arts world!"

Those with knowledge of the situation quickly add commentary to the fight that suddenly breaks out in the audience.

The sound of flesh hitting flesh was loud.

"That's a monstrous attack called Yukpo-sam! It's not flesh, but armor that protects the body. It's a martial art that can rival the Diamond Invincible Shingong in terms of self-defense!"

"But there's a side effect of gaining weight, and I heard that he can't even wipe his own behind!"

Again, the commentary follows.

Then Jang So-nam also got angry.

"Where was this crazy barbarian throwing his sword? And I didn't push him! And who can't even wipe own behind, that's nonsense!"

"Don't make fun of me! You're the only one in Zhongyuan with enough ladders! And you should also maintain cleanliness! Somehow, I've been sharing in the stench!"

"You crazy bastard! No! And I wasn't pushing, I was just breathing, and you're as light as bones, so why you're blaming me for getting pushed over!"

The commentators all raise their voices in unison.

"Who else would push a master of Unrestrained Realm? But if he pushed without malice, without any killing intent and without any anticipation, even a master of Unrestrained Realm would be defeated!"

"No matter how skilled you are, you cannot be free from the weight of your body. The well-known technique of the thousand-pound weight lifting method was a way to overcome the lightness of your body and exert the strength of a thousand pounds. It does not increase the weight itself!"

"No! Then how do you explain the skill of a master who suddenly falls from the air? The Thousand-Gun Chu was a sophisticated technique that uses internal energy to instantly increase the weight of one's body!"

"What the heck, you know nothing, you're just pretending to know and spouting out whatever comes to your mind!?"

"You don't even know martial arts, so how dare you raise your voice!"

"What, what did you say!? You little brat, are you done talking?"

On one side, a thin person and a fat person are bickering, and on the other side, debaters who are passionate about their commentary are shaking each other by the collar.

\textit{What the heck, this was a total mess.}

That was the moment when Qing frowned.

A sudden rush of air that touches your skin.

A flow that occurs when a large mass pushes through the atmosphere and approaches.

A sense built up through experience, the power of awakening.

Kkang!! Sparks fly before Qing's eyes.

The sunset and white waves collide, sending sparks flying.

Qing's body was pushed backwards.

However, because he was a statue with innate strength, he was still and motionless, so his posture was just a short line drawn on the hardened floor.

\textit{You cowards, why are you launching a surprise attack at a time like this?}

\textit{If a fight breaks out somewhere else, isn't it the law of Zhongyuan to at least watch it until it calms down, even if you don't try to calm it down yourself?}

It was the thought of a master of surprise attack.

Two swords. One spear.

Qing keeps taking steps backwards and swinging his arms.

The four colored stars traced paths and collided, scattering into pieces, and the sound of metal colliding was loud.

Aren't you a genius? No. I can handle it.

Even if it becomes even slightly dangerous, he immediately uses his Shadow Clone Technique to dodge, so he was not skilled at dealing with the situation that requires him to be on the defensive.

That won't do.

Qing grits his teeth and fights off the attacks, pushing and kicking them away.

A long sword made of single-edged iron that extends deep into the blade of the Moonlight Sword and reaches all the way to the sword belt.

Even though Qing tries to shake it off, the two swords become intertwined and rotate together, sticking together as if glued together, a tenacious sword strike.

Then, a long, thin thing splitting the space.

Qing urgently brings her left palm behind her right ear.

The swordsman's blade, aimed for his neck from the right, collided with his forearm, and a loud noise rang out, ringing in Qing's ears right below his ear.

Beep, my tinnitus was ringing.

But before he could even think about it, the single spear aimed at Qing's left flank and slashed!

Qing pushes her pelvis forward with all her might.

The spine, which had exceeded the limits of human flexibility through the ten-star training, bent like a bow.

A sharp wind blows through the deep furrow behind my waist.

In an instant, sparks fly from Qing's head.

There were three enemies, three weapons, but people had two hands.

A fist that plunged an inch deep into Qing's stomach, which was thrust forward as if asking to be hit.

Ugh, my chest tightens and I can't breathe.

However, the expression on the face of the master of the fist, Danhwacheol, was not very good.

The pain felt like I'd been punched through a wall, not a person's stomach. I immediately realized that my cervix was blocked, preventing me from inflicting any damage.

A self-defense weapon trained in the harsh cold never betrays its owner.

However, it hurts quite a bit.

In an instant, Changsoo roughly grabbed Qing's hair and wrapped it around his hand twice.

Qing, whose stomach hurt and whose hair was grabbed, clenched his jaw and made a face, tightening his neck.

The strength of the Qing was not normal.

It's not like the muscular body of a Peng family member, so you can't really imagine it until you try it.

When Qing grabs her hair with all his might, Changsoo, who was holding her hair tightly, loses his balance and was dragged in.

Then, the remaining swordsman and I made eye contact!

The swordsman's surprised eyes widened for a moment, and then he pulled his sword tightly and raised it above his head - Wedge!

The swordsman's sword cuts the blue vertically.

It was a translucent blue that was divided into eight parts.

The swordsman, feeling the sensation of cutting through the air, immediately looks around, and the sight of the Cheonhwa Sword drawing afterimages in all directions fills the air.

Various figures flying with arms outstretched, jumping into the water with arms stretched out, running wildly on all fours like beasts, galloping, jumping, and circling like swallows.

Suddenly, their eyes meet Changsu's translucent face as he was dragged along by Heavenly Blossom Sword's hair.

Why are you doing that?

I don't know either, please save me.

Among them, the blue one that flew through the sky and touched the ground regains its color.

Then, a sharp pain, as if a huge needle were digging into my brain.

Qing gasps, exhaling.

Originally, if you were to forcefully display the martial arts of a great realm of thought by simply imitating it at the peak of its power, it would naturally be followed by a backlash.

It was a recoil that I could somehow endure when I was using it alone, but it came as a subordinate because my companion was caught by my hair and flew with me.

And so, at that moment, Qing staggered, unable to breathe due to the dizzying pain.

Changsu, who had also flown in, had also regained his color, and by the law of inertia, he flew straight up and hit Qing's back.

The blue was pushed and rolls roughly on the floor.

And then I jump up and hurriedly tuck my hair into the hem of my clothes at the back of my neck.

Pulling my hair viciously?

What kind of woman was she? She needs to get rid of the peppers, no, she will get rid of them.

Born a man, you will die a woman.

Qing glared fiercely at Changsoo, who was still rolling on the floor, but then stopped.

Making ice cream was fun, but I think it would be even more fun to climb the ice wall in the snowy field in my imagination.

Even if there were three enemies, I could somehow block them, but with two, it wouldn't be a fight.

Qing gently rubs the stomach that was hit.

There will be bruises, but they are only because the veins in the skin have burst. If you tense up your abdominal muscles hidden inside, you will feel that it's okay. You will be able to hold on and bravely convey your safety.

At this point, isn't it worth doing?

Because the sum of the three does not match.

What if next time some evil or monstrous bastards get together and attack because one of your sworn brothers died?

Qing throws his sword awkwardly.

If you just let him see it, he'll probably stop the duel, saying he's grateful for the favor.

Changsoo, who had rolled around on the ground like a bed to avoid being hit, jumps up and runs backwards, shoulder to shoulder with his fellow avengers.

"Ah! Oh dear, the Heavenly Sword has missed its chance. You may be wondering. However, martial arts are originally meant to be used against those standing on the ground. The technique of cutting down those lying down does not exist."

"That's right. Besides, isn't Heavenly Blossom Sword a true martial artist? Look at her declaration that she'll face three opponents of the same level at once in a place where they can end their grudges. She's a warrior who pursues fairness with her own strength, so attacking an opponent who's already rolling on the ground must have been difficult."

"I see, that's what it was!" "So that's what it was!"

Only then did the commentary of the debaters come into my ears.

Before he knew it, both the slim and fat guys, and the debaters who had been grabbing him by the collar, were all focused on Qing.

However, it's a strangely biased interpretation.

Well, if people don't have a connection, they tend to support the weaker side rather than the stronger side, the side with less rather than the side with more, and the side with less rather than the side with more.

Plus, it's a showdown between three men and one beauty.

Men naturally cheer for beauties, and women naturally cheer for female warriors.

'She was just a young girl who was trying to fight with her life on the line against horde of enemies.'

Unintentionally, her reputation was skyrocketing.
