\chapter{Karma Comes Tumbling Down (12)}

In fact, the tongue of the Ximen Qing that was used to provoke Wang Mang was extremely treacherous.

Because Qing drank with the best scholars of the Hanlin Academy and Zhongyuan (but studied along the way) and studied all kinds of classics.

It was very malicious because it was not something he said out of ignorance, but something he said with full knowledge.

Wang Mang was not so much a red as a tyrant.

Whatever the intention, I tried to do whatever I wanted with my country, but ended up in a rebellion and was killed.

Then Jongjeongpil answered.

"Hmm, don't you know the Mohist teachings? The world was a four-person system, with equal distribution, and everyone was both teacher and disciple. Hmm, yes. Now that I think about it, this was precisely what we call universal love, universal love in martial arts."

"Ah. So you know humility……."

Qing was slightly surprised.

I didn't know you knew how to sing.

If you insist on hearing Wang Mang, why are you silent?

The Mohists are ancient primitive anarchists.

Anarchism was originally half-red, so even the primitive ancient communists are half-right.

Humility was a person who was infinitely equal to everyone.

Because all people in the world must be loved equally, marriage and blood relations are denied. Marriage was prohibited.

All children are my children, regardless of whether they are mine or someone else's. Co-parenting.

If you have wealth, you will become jealous and also show favoritism towards those who give a lot.

Prohibition of private property.

However, unlike the communists, it's not nationalization, but something that belongs to all of us, so if you need it, you can just take it without saying it's yours or mine.

"Well, it's a little different."

In fact, all ideas are pseudo-ideologies.

The word ‘pseudo' means similar, ‘sa' means similar, ‘i' means not, and ‘bi' means similar but not the same.

So, if I were to explain it one by one, I would be speechless.

Can that be done here?

If you learn martial arts to become stronger than others, how can you share your enlightenment and lift each other up?

I saw it from the distant future, and it didn't work. On top of that, it failed miserably and was treated as a joke.

Stop dreaming of impossible dreams and open your eyes.

There was no way to say it like that.

Because that would only hurt your feelings.

I don't think you'll listen even if I tell you.

Wouldn't you understand that this doesn't work if you try it yourself and it doesn't work?

Then what?

Change the route!

"I respect the will of the Great Hero, but his method was wrong."

"Wrong? Not something else?"

"Yes, you were wrong."

Qing's back, which had been hunched slightly, straightens up, his posture becomes as upright as a straight bamboo, and his eyes become dizzy.

Ximen Surinryu Women's Road. My first step.

Sit proudly anywhere.

For reference, one second was walking confidently, and this second was sitting confidently.

Then what about three seconds?

When Qing tried to match the answer, he got hit hard in the chest, saying, "How can a girl think of lying down in front of others?"

Thinking back now, I wonder if that was the extent of his kindness, but it was when he had just entered the Shinnyeomun Gate and was still a bit in love with her.

Come to think of it, he was really strict at first.

Walking like a man was called honey-bam, sitting like a man was called honey-bam, talking like a man was called honey-bam, etc.

What? So you've given up now?

Well, I want to see Master.

Three seconds was not about lying down, it's about talking.

Speak confidently anywhere.

He said that the right voice coming from the right posture was what truly has power.

"First of all, if the world was to cultivate, study, and develop together, its methods cannot be evil. Even if, in the distant future, the martial arts world becomes a single sect, those who unite in evil magic will become a source of trouble, no, a great disaster."

"Why?"

"Because to those who don't belong to the martial arts world, they'll just become a bunch of vicious bandits. Government officials, or even civilians. Even Subsimgong was like that. Since we're all under the death penalty, are you suggesting we take out the hearts of civilians or officials instead of our own?"

"Indeed. I understand. However, pure study was already tightly held by those greedy, those who already have it—yes, those with vested interests—so how on earth can we persuade them?"

"There's no way to persuade them. After all, any divine art has its weaknesses. If it were to become widely known, it would endanger those who learned it. It would jeopardize not only the sects' cherished visions, but also the families they've formed, not born from the same womb, but who share the same master and are now brothers and sisters. Even animals protect their own flesh and blood. How can you possibly try to elicit human cruelty through words?"

"Then what should we do? They've monopolized the divine power for a long time, and as you said, they've built a fortress just for themselves. So, isn't it impossible to fight against them and obtain the divine power?"

"that-"

"Ah! I think you know even without me hearing it. That's the one ghost you spoke of. If those who have nothing unite and fight against it, no matter how powerful they are, it's useless. If we burn down the fortress of those satiated pigs and tear down all the walls that stand in our way, then won't that be the true birth of the martial arts world, the martial arts world?"

Suddenly, there was a revolution in the atmosphere.

This guy was going to be in big trouble.

It's a good thing I followed you, but if I had just gone, wouldn't my name have been listed in the mission window later?

What a crisis, a red-hot land.

Or with a title like the Red Guards Rebellion.

Or, since it's joint training, do they use martial arts, airborne unit rebellion, or some kind of special forces martial arts?

"No. The blade was the most convenient tool for taking lives and shackling them with endless resentment. Such methods will never create a unified martial arts world. Bloodshed and resentment will only return, leading to an eternal, bloody, strife of divisions."

"Then? What should I do?"

"Was the Divine Art always Divine Art? All Divine Art must have been weak in its beginnings, the essence of a sect developed over generations by an ancient school. Therefore, wouldn't it be appropriate for the Great One to create from that humble beginning?"

"I am the beginning."

Jongjeongpil was lost in thought.

And then he shakes his head as if he has reached a conclusion.

"Even if we start now, when will we catch up with those who are already hundreds of years ahead? And since the privileged class won't wait, won't we just fall behind at the same rate?"

Qing was speechless.

Would someone who knows that say something like that?

What crime did someone who was hundreds of years ahead of his time commit that he now has to be held back by someone who just started?

Of course, if you are guilty, you can be caught.

But did Gupailbang commit such a crime?

When the government and the private sector are all just filling their own pockets, the only organization that maintains a minimum level of public order was the Wulin Alliance.

Qing hides her true feelings and gives a meaningful smile.

"No, those vested interests will eventually face certain defeat."

"Why, why was that?"

"In the case of the method of teaching the sacred art in prestigious schools, it's to select the most precious disciples among them and pass it on secretly, lest it leak out. As time passes, the number of masters of the sacred art gradually decreases, and the sacred art was lost and disappears."

It has gradually become a place for a small number of geniuses, and will continue to be so.

And what about the world's martial arts prodigies who cry out with a burning thirst for higher studies?

As the number of possessors of divine powers decreases, and as the study itself becomes obsolete and disappears, more and more people will suffer from hunger and thirst.

"So, in the not-too-distant future, everyone will rise from their seats and clench their fists. A true world martial arts world, where all four seas are equal, will unfold. Will you, Grand Master, prepare for that future? As the vanguard, laying the foundation for a rugged mountain path, perhaps you will witness the achievements of the world martial arts world with your own eyes."

It was a plagiarism of the logic of the communists.

If you just replace the prestigious schools and the gifted with capitalists and workers, it would be exactly the world revolution they are talking about.

At the same time, it was also the final persuasion.

It's something that will happen in the future anyway, and it's something you might not be able to work towards for the rest of your life.

So don't waste your efforts and just give up.

Will you be a wise man or a wise man?

In the legend, Yugong wanted to move a mountain, so he wanted to pass down a great undertaking that could not be accomplished in his own generation to future generations. Although he was foolish, he had great ambitions.

Hyeonro, who laughed at such a fool, was a bad person for calling him a cripple instead of saying nice things.

But, it's said that you have the wisdom to give up on things that cannot be done and enjoy life.

At that, Jongjeongpil suddenly gets up from his seat.

Then, put your palms and fists together and bow your head politely.

It was a greeting custom of Zhongyuan called Pokwon.

"I doubted you for a moment, but you truly are a giant with great ambitions. Therefore, I, Jongjeong Mo, sincerely ask for your opinion."

Miss, I'm going to go back.

What on earth was it about the random sound that made this man blush so much?

Ah. So that's why they're called ghosts.

It turns a perfectly normal person into a bloody mess, so of course the whole world was afraid of it.

"One. First, gather like-minded comrades. If you demonstrate the martial prowess of the Great Swordsman first, your comrades will follow suit."

Two, if you share each other's martial arts and insights, your imperfect martial arts skills will gradually become more complete.

And if you make this known to the world, more and more people will be inspired and gather around.

Three. Wouldn't the martial arts scattered throughout the world, gathered, supplemented, and combined, ultimately create a study worthy of being called a divine art?

"From this time on, like a fire rushing through a dry mountain, it will spread throughout the world. Only then will we be equal with those privileged people, on the walls we have all built together."

"Oh! Indeed! Are you truly a newcomer!? Now, I, Jongjeong Mo, have realized the great undertaking in which I will invest the rest of my life without reserve! Now I know what to fill this empty life with. Not a life aimed at achieving a goal, but a life prepared for future achievements!"

It was the moment when the college of engineering changed its name to respect.

Jongjeongpil was so moved that he even spit out his saliva in admiration.

however?

In fact, Qing didn't tell me anything.

Because, if you put together the one, two, three, and conclusion of the blue, it means this.

Well then, I guess I should just start a sect.

Gather like-minded comrades?

Dokgo Geom, the best martial artist in the world, was said to be teaching his martial arts, so of course people will flock to him.

I think all the ronin who hear the news will probably flock there.

Let's all work together to perfect our martial arts skills?

Well, Vision, according to the saying of the Blue Homeland, all sects without ultimate skills have always done so until now.

In fact, it's not much different from the countless sects that exist in Zhongyuan.

The only unique thing was that the membership restrictions are relaxed, and if you pay the membership fee with your own martial arts, you can enjoy unlimited access to the sect's martial arts?

Even the old prestigious schools, after completing their new skills, select people and hire the right talent to nurture peerless masters, but the difference was that they do not hide it and aim to reveal it all.

But when will the new skill come out?

If you look at Jongjeongpil's generation, all it did was establish a sect.

You go around alone, so your nickname was Dokgo Sword?

Well, from now on, you can just change it to something like Dongji Sword, People's Sword, Our Sword, Red Sword, Andokgo Sword, or Munpa Seun Sword.

Wouldn't it be obvious that they wouldn't be able to stand by and watch the martial arts they created together being abused?

Then, just one sect was born.

Dokgo Geom, who didn't even know that, was just burning with the spirit of the times that he suddenly realized.

Qing had a hard time keeping the corners of her mouth from trembling, as if she was about to turn evil.
