\chapter{Karma Comes Tumbling Down (11)}

The structure of the house loved by the officials of Zhongyuan was a manor in the style called Sihewon.

They built a square lot, built a wall, attached a building to it, and placed a garden in the center.

The more prestigious the manor, the higher the wall and the wider the garden, but the landowner's manor was more like a fortress with a wall a foot and a half high than a house.

Building and living in a mansion like this in the middle of the city was the very definition of a landowner's prestige.

Just as the commander was called a general from above, the landlord was called a landlord.

Qing inspects the house with his eyes sparkling with the professional spirit of a carpenter.

He was a sincere servant only when he was not unmanned.

Either way, the landlord's head was now in a state of confusion with all sorts of thoughts.

He was a landowner who was trying to entertain the commander, but ended up serving the high-ranking lady by accident.

What kind of woman was this that makes the commander act so trembling and humble?

From the commander onwards, he was called a general.

It usually means that the officer in charge of military service was the last to arrive.

In a country with a severe backlog of personnel, this means a woman who can either give you a promotion that's not too high, or can serve as a supporter who can wield even more power.

A member of the royal family? Or perhaps a confidant of Her Highness the Empress, the current power broker of the imperial family.

The landlord then racks his brains over the genealogy of the relationship.

The relationship genealogy was a unique personnel management system of Zhongyuan, and in the Qing homeland, it's pronounced as guanxi.

Should I tell the Left-wing Governor Nari that it would be a good idea to get on the city council line right now?

or not……

Even monkeys fall from trees and end up with rice cakes stuck in their throats if they lie down to eat them.

The landlord ended up having a very sweet dream.

So I ended up forgetting an important fact.

And when we arrived at the banquet hall, oh my.

Inside me right now-

"Oh, there are already guests inside?"

"Huh? A landlord? No way."

"Hey, sleep, just a moment, just a cup of tea-"

But before the landlord could even try to sort things out, the servant who had been preparing to serve the master inside burst open the door and greeted him.

and.

"Oh. This."

Qing was impressed.

Wouldn't the beautiful women, not wearing clothes but hanging them, be kneeling quietly and waiting with their hands clasped together?

The expression "hanging over" was very accurate, so wouldn't the hem of the garment, which should have been on the shoulder, be hanging on the inside of the elbow?

It was a drinking party to entertain the commander.

Of course, there's no way they only prepared alcohol.

They were the best flowers in the city.

Once you become a landlord, you don't need to go out of your way to hire the best gisaengs in the city.

Being the concubine of a high-ranking official was the dream of all gisaengs, so whenever the landlord held a banquet, everyone would rush to attend.

So, the gaze of the gisaengs looking at Qing was not all that kind.

What? Isn't she the type of girl who hangs out in this neighborhood?

Why do you come to someone else's neighborhood event and disrupt it?

But why are you acting like a gisaeng with that face and that body?

If I just hang around in front of the palace, I think I'll end up in front of the Emperor.

It's half caution and half admiration.

As we awkwardly faced each other, the gisaengs' clothes began to slide down.

Because clothes made of light silk are meant to flow down without getting caught on the skin.

"Oh."

Qing was amazed once more.

These two people suddenly became lost in thought.

The landlord's face was turning purple and black, and Wang Ssangryong's was so pale that his face was almost blue, as if his blood had drained from him. These were two ways of expressing the same emotion: "Fucked!"

And this was where the difference in rank arises.

Even if unmanned people are in the same sudden situation, a super-peaking unmanned person would move first to respond, and a martial artist in a state of ecstasy would move first to respond, rather than a martial artist in a state of extreme ecstasy.

If we have to be specific, the commander of the Doji would be around the latter level of Unrestrained Realm in the government hierarchy.

He was a master of conduct that no landowner, who was at the peak of his power in the official hierarchy, can match.

"conflict!!!"

Wang Ssangryong casted Gal!

It was a tail cutting that came out right away.

I did nothing wrong and had no idea.

It's all a plot by the landlord.

"Landlord!! What the hell was this!!"

"Oh, that's……"

It was a time when the landlord was sweating profusely.

"Oh. Is this a place where I can hang out too? I'm afraid I'm just barging in without any notice."

"Go!!! Landlord! Your hospitality was truly wonderful!!"

It was Wang Ssangryong who immediately changed his attitude.

"I was so impressed that I screamed. I have a habit of screaming when I'm so impressed."

The landlord was absurd and annoying.

The guy who was trying to blame me while holding a book will suddenly lose his face.

That's how thick of a face you need to be to be a commander. Not just thick-skinned, but with a perpetually thick face. Even if an arrow were to hit your face, it would bounce off. Your bulletproof face was exactly what makes you a general.

Either way, Qing gulped.

And then suddenly something comes to mind.

San-i said he would take me to Nanyang Jeil-ru.

ah!

I was so busy that I couldn't even attend the grand banquet to commemorate the second-hand Okgirin sheep.

(It hasn't opened yet. It's planned to open when Qingi goes.)

I was planning to go and have fun with Miss Peng, but if it's Habuk, I'll stop by on my way to Hangzhou and see her face.

Anyway, Qing had a good time.

The two high-ranking officials did not dare to flirt with women in the presence of the queen, which was a bit unfortunate for the gisaengs who had been aiming for the position of concubine.

And there was one person who got caught up in it by accident.

It was Jong Jeong-pil, who was Dokgo-geom and became the Red Sword (Jin).

Jongjeongpil was not the type to enjoy women, so he was not particularly interested in it.

Of course, it wasn't the same class as Changbin.

In the first place, why would a master of Unrestrained Realm, who was treated with respect wherever he goes, be hungry for a woman?

So, while drinking alcohol in gulps and glaring at the person in question, he keeps making a bored expression.

Didn't we have something to say?

Why are you so excited about women?

Qing just pretended not to know.

They say that after saving a drowning person, he asked for his bundle.

I saved you from the nagging hell, and now you're trying to stop me from playing.

What? Is it because you're red that you don't like such a fancy banquet?

But Qing has no time to think.

"Although I have entered the military, as a person who has trained in martial arts, transcending the ties of government and martial arts, how could I not respect this great warrior who achieved the pinnacle of excellence at the age of twenty? Regardless of age or gender, I have always admired and respected the great swordsman of the Heavenly Flower Sword, who accomplished such feats. Therefore, I offer you a drink here!"

"Hey, don't mention it. Wow, good."

"Me too! Although I'm a young scholar, I've longed for the martial arts world since childhood, but I've given up on it now that I'm old. So, meeting a renowned great swordsman was truly a joy, like those powerful salmon swimming against the current. So, I too will offer a drink."

"Age was just a number. It's not too late. Um, no. I'll drink well."

Kyaaaa, Qing was breathing in a cool fire.

In fact, because of my constitution of being a blood poisoner, whether it was water, alcohol, poison, or even the rotten sewer water, it was all just a way to replenish my fluids.

But I still feel good.

The two high-ranking officials glance at Qing.

The person who drinks this was not just any regular person.

In fact, the rumor that Heavenly Blossom Sword was a drunkard had spread widely.

They say that even after drinking a large amount of poison in a drinking competition, his expression didn't change at all.

So I guess I can keep raising my glass without worrying about what others think.

"I'm still at the peak of my career due to my busy military career. In terms of academic ability, I'm quite a junior. Now, sir, please accept my junior's drink."

It was a sad sound that Dokgo Geom was listening to.

Why are you being polite to Hasu when you're sitting with Chojeoljeong and Unrestrained Realm?

"Hey, you've gone too far. Kwaaah, the instant noodle soup? Right?"

"Ah! You know about the Jikmo Noju! Shandong was known for having the clearest water in Zhongyuan. Didn't the Qin Shi Huang once say that if there was an elixir of life, it would naturally be found in Shandong? Therefore, the best liquor was made with the finest water. The world's most exquisite liquor was none other than the Jikmo Noju, made with the water of Mount Lao. Here, have a drink."

"Well, Mount Lao. Miss."

Qing gulps down the alcohol, yaaaah, Mount Lao was not that great, but alcohol was really good.

So, when the cup of Qing was empty, the commander on the left and the landowner on the right would watch each other closely and compete to fill it.

The gisaengs on either side of Qing are ridiculous.

If you guys were going to fill all the glasses, why did you call us?

Is this a drinking party or a training session?

When I sit down, I get up to fill my drink, then go back and sit down again, then get up to fill my drink again.

Is it okay to exercise while drinking?

Either way.

Qing said it was really fun.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Every month, every day.

Jongjeongpil asks Qing, the theoretical teacher of Gongdongmuhak.

The commander and the landowner are the greatest officials among the officials, and their power was like that of a ferocious tiger, and everyone fears them. They also rule over a mountainside and are as arrogant as an emperor.

But why do those criminals act like dogs to you, turning their bellies over and acting cute?

Qing answers to him.

It was not right to judge by only one side, for this was not based on any gain or convenience, but simply on friendship as friends who have traveled together, however briefly.

Qing was talking nonsense.

As the princess of the Ximen Qing, she did not treat her inferiors well, so it would not be an exaggeration to say that she felt like a friend she had met while traveling.

"Well, then. I won't ask any more questions."

Jongjeongpil answered.

It means that they will just let it go.

So, again.

Jongjeongpil (omitted) asks.

"You clearly envisioned a dreamlike future where the entire world's uneducated people would share their knowledge and ponder together. But was that merely a lie, meant to avert an immediate crisis?"

"Hmm. To be honest, I guess, um, yeah, right?"

Qing answered while observing the situation.

However, Jongjeongpil did not seem particularly angry or disappointed.

"But after hearing it, I realize it wasn't something that came out of mere thought. So, did you come up with that idea yourself, or did someone else hear it and somehow remember it?"

The engineering department naturally descends to the lower department.

I didn't really want to go to Qingdo College of Engineering, so I didn't really pay attention to it.

"Hmm. Let's see."

Qing chose her words.

That furry guy probably hasn't even been born yet.

Isn't he? He's such an old man, he must be writing a book by now. Hmm, how would I know?

Even though not even Furbo's great-grandfather was born yet, let alone Furbo.

How would Qing know that?

But that's not enough to silence Qing.

Because the Ximen Qing's mouth was at a level where it can be considered the best in the world.

"In the past, Wang Mang said, 'The reason people fight with each other was because they covet each other's property. If they didn't have property, they wouldn't fight. Therefore, I intend to seek peace for my world."

In fact, Wang Mang was not a communist, but simply a person without possessions or a complete possessor.

People are fighting over property.

So I will take all my wealth for you.

Then I'm rich. You guys are poor.

As a result, he was beaten to death by a group of beggars who rose up, but anyway.

"How can you say that it's a waste?"

Jongjeongpil's voice was slightly offended by that.

Wang Mang was in charge of the communists in the Four Great Ilbomen of China.

For reference, the rest are Dong Zhuo, who was in charge of body fat, Cao Cao, who was a married woman, and Sima Yi, who was a traitor.

In fact, Sima Yi may feel a little wronged.

Not only are all the idiots from the four major branches of the central plains traitors, but if they don't rebel, it's obvious that the old people will be destroyed by some bastard who ruined their children's farming.

If I had to say, it was a treason for a living.

However, the reason Sima Yi was synonymous with treason was because he committed treason not once but twice.

Once in one, once on top.

Anyway, Jongjeongpil was hurt.

The thought that he truly admired and wanted to make it his life's creed came from Wang Mang.
