\chapter{Karma Comes Tumbling Down (13)}

Jong Jeong-pil's steps as he leaves the landlord's luxurious private residence are smooth and unobstructed.

I saw a new world to reach, and I knew the way to get there.

The new era may be too far away to be seen with these eyes.

But that's why I can live my whole life to the fullest.

The path ahead may be too rough and dangerous, a thousand-foot cliff on top of a steep slope.

But it's difficult, so it's worth the challenge.

So how could one not be excited as a general?

It was a very pleasant walk.

Before Jongjeongpil left, he thought about the last conversation they had.

'So, what was the martial art that Teacher previously revealed in the stone chamber? This disciple, upon examining the Qi flow, discovered that it was indeed a complete and well-established divine art.'

'Ugh. Teacher? I can't accept that.'

'It's said that when three people walk together, there's always a teacher. But isn't it true that, in the Teacher's teachings, there's no distinction between teacher and student, and that they learn from each other and strive together? Therefore, we shouldn't address you as senior. However, addressing you as peers would also be inappropriate, as there's the matter of allocation. So, what do you think, Teacher?'

"…Just do whatever your heart desires. Do whatever you want to do with your life as a great warrior. I already have a Master, so I will only support you in my heart."

'Yes. So, what about that new skill?'

'Oh, that. It's just a nameless Fairy Art. Oh, but… it elongates and rounds the body's curves, so it might be a bit difficult for a man to get used to it, right? Of course, there are no side effects up to the Second Movement, so you can used that.'

'Indeed! The Fairy Art, trained by the most beautiful woman in the world!'

Jongjeongpil was truly impressed.

The teacher's beauty was truly the best in the heavens and the earth. The fairy art that the teacher has mastered was a divine art, a treasure that all women in the world desire to possess.

And it doesn't matter if you use it.

It means that there were no lies or tricks to twist the knot.

She unleashed such perfect divine power on those evil groups who had gathered to monopolize magical power!

How dare you doubt such a noble teacher!

This foolish old mab couldn't see properly even with his eyes open!

Only then did Jongjeongpil understand Qing's reasoning.

Although she had set her mind to it, she had already joined the sect and made a name for herself, so hse could not betray the sect that was like family to her, so she just stayed.

He understood it very arbitrarily.

This successor originally sought to restore freedom to the new people through revolution through struggle. He believed that this meant shedding blood, thus transforming the world with the noble color of red. He believed that the liberation war of communist unification was the right path. Thus, he sought to raise the banner of the Red Army.

'omg.'

"Are you surprised? But not anymore. Not with blood, but with will (意), not with change (化), but with togetherness (和), and thus we will change the world. Our name will be the Harmonious Will Fist\footnote{意和拳;Yihequan}! Not with war, but with enlightenment—this was the righteous movement!"

Then the teacher tilted his head.

'Huh? What was it? Why does it feel familiar\footnote{It sounds the same as 義和拳/ Yihequan, the secret society that carried out the Boxer Rebellion}? It somehow rolls of the tongue so well.'

'Haha! It looks like the teacher really likes it too!'

do.

The smile never fades from Jongjeongpil's face as he sets off on his journey.

Where to go now?

First, let's gather the thirsty ones and the ronin.

Yes, it would be nice to meet Brother Manjeoksal.

As a brother who took up the sword to protect the common people, the spread of divine skills will also provide the common people who are falling behind due to lack of martial arts skills with the strength to protect themselves.

So, wouldn't you also be willing to join in this noble cause?

Since I happen to know the peerless fairy godmother, I think it would be good to meet the older brother who wants his nephew to learn the fairy godmother.

Even that crazy guy was serious about martial arts, so I guess I can bring it up.

Povidone, that guy was no good.

Even if we just eat together, isn't that guy the type to show off his gluttony using that jerky as an excuse?

He still needs to wake up because he's a greedy bastard with a lot of flesh.

Many names flash through my mind.

Since we haven't done anything yet, wouldn't there be an abundance of things we can do?

So, Dokgo Geom, who no longer seeks to be alone, sets out on a journey calling himself Uihwa Geom.

However, no one knew what his future would hold.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

The military base was located within the southernmost wall of the Baekha River, which flows up and down the west side of Weifang.

It was a wide open space that was originally not used and was used as a market for merchants.

A market was being built in a military base in preparation for emergencies?

You might find this really odd.

However, merchants must pay rent even when using ownerless land.

And the landlord was a real fountain of life, with gold and silver springing up from nowhere.

For reference, a flower pot was a mysterious treasure chest that continuously produces wealth.

Originally, it was a water tank used in ancient times when building the Great Wall of China. A tank to hold river water, a sewage basin.

The water jug ​​was so big that no matter how much I used it, the water never ran out, so I enjoyed it endlessly.

So the meaning changed to infinite treasure chest and the letters also changed to match the meaning, Hwasu-bun!

Anyway, if you look closely at strange things, it all depends on the time, so it can be said that there are no strange things in Zhongyuan.

The poor merchants lost their stalls overnight and had to leave their vacant lots empty, but Qing had no need to feel sorry.

It was simply the rightful end for an illegal street vendor, and also because being pitiful never means being good or right.

So, a new facility was built in the military camp where the merchants had left, and it will become a dueling arena.

Are you dissatisfied that I impersonated you and lied about having magic that doesn't exist, people of Zhongyuan?

If you're in trouble, jump in.

As Qing had declared, the place where life and death would be decided had opened.

Even before the first duel took place, the auditorium was already overcrowded.

Watching a fight was the best thing to see in Zhongyuan.

And this was the second time I've seen a beauty.

But the Heavenly Blossom Sword, which was said to be closest to the best beauty in the world, was waging a life-or-death battle?

How can you stand this?

So, soldiers, breast-feeders, unmanned people, and even snack vendors who never miss an opportunity!

The battle of life and death hasn't even begun yet, and there's no place to stand.

By the way, when did the Cheonhwa Sword come out?

You said she was that pretty? You saw her? What did she look like?

Pretty.

No, explain. What do eyes look like?

Pretty.

What about the nose?

Pretty.

What are you wearing?

Pretty.

No, talk shit, kid. They're all pretty.

It's just, it's really, really pretty, I don't know how to describe it. Just look at it.

Oh, it's coming out! Over there! Over there!

And those who were still unaware of Qing's beauty confirmed the truth of the rumors.

Hmm. That's pretty. That was an accurate expression, I thought.

It happened here and there.

Meanwhile, half of the circle surrounding the arena was occupied by soldiers, so Qing made his way through the space and looked around at the people.

What the heck, it seems like the whole city was out in force. Isn't there anything to do?

Isn't it the busy farming season? Aren't you busy?

Well, it doesn't matter anyway

Qing takes a deep breath.

"As I said, a tangled rope can't be used unless it's untied. So, I'll resolve this long-standing grudge here. Those who harbor grudges, those who don't believe or understand what I'm saying, come forward and find the conclusion in Wulin's way."

The people are dumbfounded by him.

That would be the case, as the soldiers surrounding half of the arena were already armed and holding spears and swords.

As if they were going to charge in right away if she was at a disadvantage.

On the tall watchtowers erected around the area, wouldn't soldiers be holding bows or leaning against iron oars to aim?

As if they're going to shoot if she was at a disadvantage.

"Wait! Heavenly Blossom Sword! Before that, I have to ask. What are those soldiers standing in the watchtower behind you doing?"

"Oh, those guys. They're watching from up high."

"Why did they take up the bow?"

"Isn't it said that weapons are the companions of the military? How could a soldier abandon his weapons? Isn't that right, gentlemen?"

"That's right!" "That's right!" "That's right!"

The sum matches and a loud answer rings out.

"Didn't you said that it's a coincidence you traveled together?"

"Because it's a coincidence?"

"That's it. No, you can tell just by looking at them. Otherwise, why would they be here all this time, flashing their swords?"

"Hey, look here. A lot of people from the neighborhood have come to see the sights, so what's so strange about soldiers coming to see them? You're all here to see the fights, right?"

"That's right!" "That's right!" "That's right!"

"Now, look. Even the military says the same thing."

What can they say if the military insisted on it?

They were speechless an dumbfounded.

"Okay, now let's untangle this knot."

Anyway, we couldn't communicate with each other.

Even if there was no magic absorption, there are those who don't believe it, or those who say that they are just bystanders when the military was laid out.

As Qing stood there quietly, his sword drawn, no one dared to step forward for a long time.

Well, that was only natural.

If you were going to ask for resentment anyway, it would be better to do so after you had sufficiently observed the opponent's inaction.

We need to see if real soldiers are just watching.

Also, we need to see if the Heavenly Blossom Sword was easy or not, and if it really has the skills to deal with one Unrestrained Realm master or three top-tier masters.

Then suddenly, someone popped out.

There was not a single bit of flesh on his exposed body, let alone any muscle, and he was bald and skinny, as if he were just covering his bones.

"Strange Monk\footnote{怪僧; Guaisheng}!" "Strange Monk!" "Amukhaprap!"

The knowledgeable onlookers shouted at him.

Watching a fight was the greatest pastime in Zhongyuan, and so the ability to read the situation was one of the prides of the Zhongyuan people.

So, as soon as they come across something they know, they shout at each other, saying, 'I am the one who knows', 'I am the one with the most insight', and they are impatient to be born. It can be said that they are like fast carriages racing to be the first to arrive.

\textit{Dammit, an Unrestrained Realm Master from the very beginning.}

Qing was a little nervous.

Usually, when someone was about to make a life-or-death decision in front of people, they tend to state their business first.

So, all the onlookers soon became quiet, and the incident calmed down.

Everyone watched the monster with bated breath, waiting for his mouth to open.

And finally, the Strang Monk's mouth opened.

"Who pushed me!? What kind of person without a father or mother knows no manners. In the name of Buddha, I will never forgive you! This was killing approved by Buddha!"

He didn't come out by his own feet, someone pushed him.

But you don't forgive in the name of Buddha? Does that make sense?

"Did you get pushed out, Senior Sftrange Monk? Or did you come here to resolve a grudge?"

"Exactly! That's right! I will verify this! If Zhongyuan woman was in danger, she will use Demonic Art!"

"As I said before, the trap was a despicable scheme of the Blood Cult."

"It's impossible to know. Anyone in danger will inevitably become violent. If they have Demonic Art, they'll use it. If they don't, they'll die to prove their innocence."

He said that he would continue to be suspicious as long as Qing did not die in a life-or-death struggle.

Qing was speechless.

\textit{Does that make sense? What kind of witch hunt was this?}

A monk who hunts witches?

He was truly a strange monk worthy of his title.

Then he turned his back and took his place among the onlookers again.

Boos of "Oooh" rang out, but the Strange Monk didn't seem to care at all.

As they were doing that, the three people finally quietly stepped forward.

His eyes were already filled with murderous intent, and when Qing looked at him, his chin moved greatly, meaning he was already tense and ready to fight.

However, the three of them are in a delicate position, so they don't really exchange glances.

Qing quickly came to a conclusion.

She said she would accept up to three Transcendent Realm Masters.

It seems that the three of them, who probably don't know each other, have joined forces to take revenge.
