\chapter{Karma Comes Tumbling Down (8)}

The ancient name of Weifang was Qingzhou, and the elite Qingzhou soldiers commanded by Cao Cao, who was in charge of the married women of the four great scoundrels of Zhongyuan, Mangtakjo, were soldiers from this village.

However, at that time, it was not called Qingzhou but Beihai, and the governor of Beihai, Kong Rong, a direct descendant of Confucius, was from this village.

When you say Kong Rong, you might feel like an ordinary person who doesn't have much of an impression.

However, he was the most brilliant figure in the Later Han Dynasty and a true scholar who was hard to believe was from Zhongyuan.

This was revealed from Gongyung's groundbreaking remarks.

"Why should I respect and serve my father? When you think about it, he simply took a step forward to satisfy his own sexual desires. And why should I respect and serve my mother? She simply took out what was inside her, like excreting feces and urine."

In the end, Cao Cao used these words as a basis for exterminating Kong Rong's three clans, claiming that there were unfilial sons in the world.

However, it's an absurd accusation because Kong Rong was a true filial son who was known for his filial piety.

The word "Gongyung" was not a curse on parents.

This was a famous passage that criticizes the fact that filial piety, which was the teaching of Confucius and our ancestors, does not come from simple filial piety but has become a political maneuver to show off to others.

For example, Yuan Shao, who monopolized the love of all the scholars of Zhongyuan by three years of mourning.

And the unforgettable Cao Cao.

He was a world-class murderer who committed genocide for political reasons to weaken the power of the West, but he sold his dead father to defend himself.

Is it because it's such a city of fusion?

This was the procession of Princess Yeonsul, the mother of the world.

Originally, the emperor was the father of all people in the world, and this genealogy applied to all blood relatives, regardless of personalities.

So, just because the Emperor was their father does not mean that the prince and princess are siblings, and the prince and princess also have the status of quasi-father and quasi-mother to all people.

Of course, you should kneel down, bow your head, and be in the posture of a child supporting his parents.

But instead, they were just holding sharp blades and looking at the army with indifferent eyes. Could they be citizens who have inherited the spirit of Confucianism?

"Oh, Madame. Look over there! Aren't the people of Weifang preparing to welcome their Madame? What a noble people they are! I wonder what kind of welcoming ceremony they'll be holding!"

"That's not a welcoming ceremony, it's preparations for an execution. Probably."

They were martial artists who were looking to acquire the world's best magic.

Where on earth do you see that welcoming ceremony?

For reference, the word "shiriphada" means to stand with an adult, and if you came out to greet someone, it's a polite expression meaning that you came out to greet them.

Anyway, before the gates of Weifang, two groups of armed men, the military and the unarmed, get closer to each other.

But surprisingly, there was no tension.

Because it's an non-interfence agreement.

To the military, the martial artists are just a bunch of thugs with swords.

For the martial artists, the military was a huge trap that will have repercussions for the entire family if touched.

And so they got closer and closer.

"Hey, isn't that lady on the white horse pretty? What was she? Is she a Madame?"

Madam was a term used to refer to a woman who holds a government position.

"Pretty? Where. Oh."

"Isn't this a joke?"

You're pretty? Oh. Where, where, over there. Really? What's wrong with you all? Isn't it just because you're in the military that you're pretty? You little shit, you're not first-class, you're second-rate, you don't even have good eyesight. I smell like you're trying to scam someone, etc.

The rumor that a pretty woman was coming to the warriors who were bored to death while waiting for the Heavenly Blossom Sword spread like wildfire.

And it was really pretty.

It was an odd sight for a fairy to be riding a white horse, but if you have a pretty face, no matter what you wear or what pose you take, it will look perfect.

And then.

"No, it's the Thousand Flower Sword! Why was that girl over there?"

The gazes of the martial artists are filled with three shades of bewilderment, absurdity, and disbelief.

No, why was she appearing among the soldiers?

And they are not just any soldiers, but soldiers carrying the flag of the commander.

And, wearing a general's hat and carrying the commander's flag bearer behind him, it was obvious to anyone that the commander was in the lead, and the blue was standing next to him.

And then, as if the two were whispering something, signal flags started to fly here and there and the military march slowly came to a halt.

Look at these kids' expressions.

Qing chuckles and looks around as if she was looking at something.

Everyone had expressions like they were stamping their feet, but they couldn't do anything and just stared at each other, asking, 'Why is she coming out of there?'

So how could Qing not say a word of wisdom?

"Hello, everyone! You know me, right? Ximen Qing."

"Three Headed Beauty!" "Heavenly Blossom Sword!" "Heavenly Blossom Witch!"

That damned three-headed beauty, ugh.

But what about the Heavenly Witch?

Cheonhwa Witch was the newly updated nickname of Qing.

Since she learned magic, she's a witch anyway.

The most beautiful witch in the world. I can't tell if that's a compliment or a derogatory remark.

Qing looks down at the people from his horse with a bright smile on his face.

The clever captain's horse also takes a cool horse stance and looks down at the warriors together.

The warriors who saw the beauty of the properly equipped Heavenly Blossom Sword were immediately impressed.

however?

Why was that smiling expression so mischievous?

Hehe, like, "I'm going to die from this medicine."

Since the Heavenly Blossom Sword stood still, its intentions were clear.

If you have something to say, say it.

But not everyone has a say.

It was an unspoken rule in martial arts that if there was a master who knew the master, the lesser ones would have to bow down to him.

The sewer was sad in one way or another.

This was why you have to become an expert.

"Look here, Heavenly Blossom Sword. You-"

"Wait a minute. Who are you?"

It was one of the chronic diseases of experts.

Not only do all the people in the world recognize them, but they cut off their self-introductions and get straight to the point.

"Ahem. My name was Widaemyeong."

"Ah! You're the great swordsman of Manjeoksal. I, Ximen Qing, the last of the martial arts world, would like to offer my greetings. Please forgive my rudeness in not being able to dismount due to circumstances."

Qing bowed politely.

Manjeoksal Widamyeong.

He was also a member of Cheonhaorang, and was classified as a member of the Jeongpa faction among the Jeongsa factions.

I heard that he was given the nickname of Manjeoksal as a show of respect because he achieved the feat of cutting down only the Japanese pirates.

Widamyeong looked a little dumbfounded at Qing's polite attitude.

According to the assessments of the warriors who survived the Mount Lao incident, she was a witch with cruel hands, who enjoyed murder, and who excelled at deceiving others.

This was the most accurate assessment of Qing so far, but Widae-myeong begins to doubt the truth, wondering if the rumors that the Jeongpa's divine dragon was a witch were wrong.

The truth was this difficult.

"I heard you've falsely impersonated and slandered others, and to seek forgiveness, you must travel through five cities and through a bloody journey to Hangzhou. So how can you possibly appear under a military escort?"

"You misunderstand. It's just that military training was over, and a girl was being escorted by the military. How can a commoner privately use the emperor's army?"

Usefulness means using something that belongs to someone else or was not for its original purpose.

So, to summarize what Qing said, it would be like this.

I was just passing by, and the soldiers happened to pass by too!

But you know it's not just the military, right?

Hearing the name of Weidamyeong was shocking, my nose was blocked, and I am speechless.

If I had been a little more absurd, I might have been able to successfully block my entire face by closing my eyes, so it would be a shame that it was a little lacking.

"Uh, um. So, um. So, from now on, you're saying we'll move separately?"

"Uh. I'm constantly moving separately. The military was just training the military. Right, General?"

"Yes. Yes. That's right."

Wang Ssangryong agreed with him.

The bar of absurdity of the unmanned people rose even higher.

If you move separately, why are you two pretending to be close and talking?

Anyone can tell we're related!

"Well, General. It's truly impolite for a commoner to inquire about the military's schedule, but will the military's future plans be kept a strict secret?"

"No. Training should be like real combat, but the people facing the military might become anxious, so you should reveal the schedule to anyone under the sun who asks. The Western Army will remain in Liu Bang for four days before heading to Im Gi-hyeon. This training has been planned roughly six months in advance."

"Wow! What a coincidence!?"

So, coincidentally, our schedules are the same again.

But this training was planned six months ago.

The people who were listening to the grim news finally closed their eyes tightly, covered their eyes with their hands, or wiped them away.

It was the moment when the entire face was successfully sealed.

"That, haa."

Widae-myeong tries to say something, but his mouth was blocked and he can't continue speaking.

So what? I should tell you.

"Now, everyone, I'm sure you have a lot of questions, so I'll clarify them for you now! First, do you remember the secret technique of learning the cursed magic of the Heavenly Blossom Sword Ximen Qing and the Absorbing Magical Art?"

The unmanned people quickly opened their covered eyes and looked at Qing.

It was a change of attitude, almost like the Sim Bong-sa of the Far East.

Suddenly, the atmosphere changed to a public discourse.

"The answer is, no! I came simply to erase that cursed magic from the world!"

Woof at him!

There was a barrage of jeers, such as telling people not to lie.

Qing was being treated unfairly.

So this was how the truth was suppressed.

"Wasn't it suspicious from the start? I killed that thief, the master of the Lulin, and obtained the Jangbo map, which gave me information on that vicious magician. But there are several copies of the same map. Does anyone here have Jangbo maps?"

At the part where the green forest chief was said to have been cut down, exclamations erupt here and there.

Because he personally confessed to the fact that the rumor that Heavenly Blossom Sword had cut down the leader of the Green Forest was not very credible.

Qing grabbed the Jangbodo and waved it high.

A few people react to it.

"Huh?" "Me too!"

"Look at this. There are several identical maps, and what about the rumors you've heard? How could rumors of such a hidden, world-class magic spread so widely? Unless someone deliberately spread it."

A commotion spreads around him.

One of the dogs screams!

"Don't make me laugh! Then why didn't you reveal it? Why did you insist on impersonating someone else and committing the murders?"

But Qing was calm.

"The only thing I did wrong in that act was that I assumed someone else's name. Now, listen. First of all, you crazy girl, was that a lie?"

Even though she speaks of herself as a brainless, beautiful girl, Qing was confident and has no shame.

Because when it comes to super brainless girls, it's actually funny, so there's no particular hesitation.

It might be embarrassing to say that you are a peerless beauty yourself, but the super-beautiful girl was full of playfulness, so it wouldn't be that bad, right?

Normally, if he said something like that out of his own mouth, the crowd would be shocked, but the crowd was more or less convinced.

Because it wasn't a wrong statement.

"Second. Yun Yuanying was once a martial arts patrolman, but she was a witch of the Blood Cult who destroyed her family and joined the Blood Cult."

The unmanned people nodded again.

"Third. If the unmanned people simply risked their lives for a specific purpose, and if such acts were considered slaughter, then the martial arts world would simply become a mass of murderers. Don't you think so?"

This was also persuasive, so some nodded in agreement.

Of course, the thoughts of those who have been affected by it, including family, relatives, friends, and acquaintances, are different.

"How can it be a matter of life or death for a master like you to slaughter a weakling!"

"Then what about the six renowned martial arts masters who joined forces against me? I don't know about the other two, but Jeolnaksungjon, Povidon, Dokgogeom, and even a monster monk. They joined forces to capture a single, supremely skilled martial artist. So, I imagine they, too, attempted a brutal massacre."

How dare you bring up the petty art of painting!

If it were true here, it would be tantamount to giving the Unrestrained Realm master the right to legally (or not) commit honor killing.

The audience shut their mouths tightly at that.

Of course, you can't say that Qingman was petty.

The reason why those who kept their mouths shut when Qing was at his peak and brought up Unrestrained Realm were also petty was because they were all the same.

In fact, if you can talk this much, Qing's mouth was close to the best in the world.

However, everyone was shouting "Magong, Magong" and thrusting their swords first, so I just rolled around and ran away.

but?

The army was behind me now.

So how exciting would that be?

Qing was very excited and was chattering.

"And there's something else I need to tell you. I've already revealed that I'm mastering five of the most vicious magic arts, or rather, the absorption magic arts, which was a misunderstanding. So, there must be some ridiculous misunderstanding that I'm mastering four of the ten great magic arts."

"What a misunderstanding! I saw it with my own eyes. Swinging a sword and a black water sword, spitting out purple lightning, and with a wheel-like demon eye in her eyes! How can a world-class witch, who has gathered four of the world's ten greatest magicians, be so confident?"

Ah. That kid must have been in the stone room.

Huh, four? Are there really four?

But Qing just laughed.