\chapter{Karma Comes Tumbling Down (16)}

For a while, it was quiet, and only the sound of the wind blowing and the birds flapping their wings and crying filled the arena.

After a long silence, the expressions of Danhwacheol and the swordsman harden.

If three people can't defeat one, there's no need to fight with just the two of them.

But isn't it already a matter of life and death?

If they wanted to get out of there, they would have to beg for their life in front of all these people.

For a Zhongyuan person, begging for one's life from one's enemy is, in fact, a greater humiliation than death.

Danhwacheol and the swordsman exchange glances.

This made Akmun Danhwacheol prepared for death.

The swordsman's wavering eyes seemed to be begging for his life.

But didn't you say to fill one person's shoes rather than to end a life-or-death situation that had already been decided?

The Heavenly Sword has already gave handicaps, so if you beg for your life here, you will become the world's greatest idiot.

The three of them attacked a young girl and were defeated.

Even with a female warrior, and without resorting to cowardly means that were taboo?

The only way out was to end it with death, without becoming a laughing stock as a tragic avenger.

Besides, if they ask her to spare their life, would she actually spare them?

For a person of Zhongyuan, revenge means that the greater the humiliation he has received, the greater the honor he receives in return.

The principle behind King Goujian of Yue, who ate the feces of his enemy, being praised as the greatest avenger, was that anyone who does not seek revenge after suffering such humiliation will be remembered in history as a fool.

So, if you knew that if you spared him, it would definitely be a cause for trouble, but who would spare him unless they were a fool?

So, the swordsman's eyes gradually turn a sad light and stop vibrating.

He accepted that he was at a dead end.

If no one comes out, the two of them will just had to win.

That was when.

A warrior walks out and stands shoulder to shoulder with the two swordsmen.

"I am Master Yoo Seung-chan of the Guryongbang. It's unfortunate that you are not in perfect condition, but I, too, must have a head to offer up on the altar for my students."

"If you can."

The sound of weapons clashing was loud again in the arena filled with four people.

The blue rolls and rolls on the floor.

Deeng, the sound of the Buddhist bell.

The swordsman who was properly hit by my method falls to the ground with blood gushing out of his mouth.

The things inside the body that had melted due to the concussion continuously poured out as blood.

But I hope it goes without any pain.

It seems like he was sending me to Buddha in one go, as if he were an image of Buddha.

Hmm? Are these the words of Buddha? Are they correct?

Qing tilted his head at the imagery of the Tathagata Palm.

After the swordsman left, the person who took his place was a man named Myeongjunsa, a master of the fluent Yuyeopdo.

The fluttering blade causes changes that are not suitable for the Tao, so it's not easy to clash weapons and deal with it.

Even if you hold on with your body and grit your teeth, the skin that cannot be helped was torn and the uniform was dyed red.

Suddenly, a fierce light flashes from Qing's eyes.

In an instant, the blue sword spins around, was caught in reverse, and was lifted upside down. It twists and turns like a snake and digs into the back of Yoo Seung-chan's neck.

The 108 Swords of Asura. Fifth Movement.

Poisonous Fangs.

It's not a magic spell I intended to use on purpose.

It just unfolded naturally.

Because the enlightenment that was right in front of him whispered to him through the image of a demon.

Have you seen the fight between the beasts?

For wild beasts, beings of a ferocious kind, do not care for themselves in battle, for every battle was a life-or-death matter of nature, a matter of life or death.

So, even though the beast was torn and ripped apart and bears a fatal wound that will ultimately lead to its death, it does not cower in pain, but instead becomes angry and explodes with wildness.

My whole body, broken and bruised from being beaten, my muscles cramping and aching, my skin cut and stinging, all of these things instead resonate with a strange pleasure.

A strange surge of strength and a smile on my lips.

Man was also a beast.

Fight like a sura and go through a bloody path to become the king of beasts.

There was only one master on the mountain slope, so kill all the wild beasts, feast on their corpses, and proclaim that the world was your domain.

There was a ferocious wildness in Qing's eyes.

Yellowish eyes with vertical slits.

At any moment, the ferocious killing intent of a beast was seething and boiling throughout my body, making me feel like my chest will burst open and explode.

"Whew."

Instead of the roar of a beast, Qing lets out a long sigh.

Yes, this was the Demonic Arts.

There wasn't a single one of them that was easy.

But a violent urge to bite the necks of all the unmanned beings boils over me right now.

Wouldn't it be a bit awkward to be swayed now?

If the Master knew, he would have given that bitch a carpet bombing, saying, "How can you be running wild like an animal?"

The divine power of the Juyangsesimgyeong Shinnyeomun reacts to the will of the Qing, clouding her head.

Emperor Yan Shennong was an old emperor of Zhongyuan, so he was a very conservative and old-fashioned person.

It was only natural that the Juyangsesimgyeong, which such a salt merchant made for his daughter, would calm his mind and awaken him to composure.

The blue pupils of his eyes were once again dyed with the clear color of Taoism, but still did not erase the single ray of brute light.

Pain into strength. Like a beast.

This was exactly what I need right now.

Qing declares arrogantly.

"Next person."

The person who responded was Jang Balsan from Ganghwa, Honam Province.

He was a giant who wielded a vicious iron club with thorns on both ends.

And again the blue breaks and rolls.

And then at some other moment.

A sword that stabs, aiming for the heart.

At the same time, the thorny iron club aimed at the shoulder and the splendid waves of the leaf blades pouring down dizzily.

Blue's eyes sparkle.

Rather, he takes a step forward diagonally, pushes the sword face into his side, and thrusts in the heavy blade of the Moonlight Sword.

The moonlight sword, which had dug into the enemy's belly, came out through the nearby side.

With a hissing sound, the weapons that had been put on hold to eliminate one person attack the blue.

The blue's shoulders are folded at an odd angle, almost like a cut-out, and fall forward.

It was as flexible as a creature with almost no bones.

A young iron dagger swept through the air.

But what about the back?

In an instant, a burning pain, as if a huge flame had risen up from the back, struck Qing.

The appearance of the back was truly miserable, with the scars densely packed like the character for "鬱".

\textit{Ugh, it hurts, it hurts. But I can bear it.}

\textit{The back muscles, um. seem fine.}

\textit{Should I say that I did a good job of defending against three Transcendent Realm Masters?}

\textit{I'm more concerned about the annoying sneeze that barely touches the roof of my mouth and then goes down, and the realization of harmony, rather than the injury.}

\textit{Dammit, I think I almost realized something.}

\textit{The real end, the exact end of something.}

A woman covered in rags and blood, but still beautiful, holds up a sword.

"Next person."

Did you say it was the season of short hair?

Qing stretches out his palm to the bastard's face.

The thumb penetrates the clown's jaw and swings the tightly held head, slamming it into the oncoming river.

Shash, I couldn't open my mouth because of the terrible pain of having a hole punched in my clown's neck.

The entire body was covered in a gorgeous maple leaf that depicts the changing of the world.

"Next person."

Now there are none of the original three left, but there are still three enemies in place.

When did your head get broken?

Ah. That guy with the iron club got hit by that guy. What was his name? Balsan, Jeong Balsan? What was it? Was his last name Jeong? It just sounds weird.

He had his leg cut off with a club.

There were large blood vessels running through the thighs, and there were no doctors in the arena, so the blood cooled down, forming a puddle on the floor.

Next person.

Wow, I think I vomited a bowlful of blood.

I underestimated a punk who was rushing at me with his bare hands, but it turned out he was not a martial artist, but a master of qigong.

Pretending to be a martial artist was so fatal.

No, are you smart?

Who in the world wouldn't let their guard down when watching a dancer?

However, Qing's internal energy has long since surpassed its peak.

Since I tried my own method on a master with greater internal energy than me, I guess it was because I judged that his internal energy had depleted after a long fight.

Due to the huge difference in internal energy, the energy and blood flowed backwards, and without missing a moment, Qing pushed in his true energy in the opposite direction.

All of a sudden, the skin and muscles burst open, exposing the less-scarred arm bones.

I was screaming, and it was only after my throat was cut that I finally stopped causing noise pollution.

Next person.

She was a rare female martial artist in the martial arts world.

She said she would avenge her husband, but as the saying goes, when a woman holds a grudge, frost falls in May and June, and even though things didn't go well together, she took advantage of the gap and poured out secrets.

She set a new record for surviving five human transformations.

But as was often the case with those who throw memorization weapons, three of them hit the same avenger and ended up in a life or death situation, so it was not recognized as a record.

Next person.

The next avenger deceived the realm.

Not the peak, but the peak of the climax.

And as soon as the fight started, he surprised the female warrior of Sapa and stabbed her with his blade. This was not Qing in the first place, but revenge for his brother who had died from a poisoned blade in the previous duel.

And then I found a poisonous dagger stuck in my stomach and I collapsed, vomiting blood.

The rest, who suddenly rushed in alone, were beheaded with one stroke of the sword.

It's supposed to be three against one, but the remaining two are fighting amongst themselves.

For that reason, Qing stood alone.

There were twelve gruesome corpses on the spot.

There was no longer any slenderness on the upper arm below the exposed shoulder.

His eyes were red with blood, his lips had burst several times and blood clots were visible, and his swollen cheeks were bruised.

His hair was disheveled, and his martial arts uniform was now missing a single spot. He wasn't wearing anything, but was soaked in blood and clung to his body.

However, the gazes of those who looked upon this female warrior in such a miserable state were filled with only respect.

Of course, limited to onlookers, I should start getting out there and get my appetite back on track with these despicable Sapa guys.

Even those who shake their heads with tired eyes.

The audience, who always cheered and shouted for commentary or bets, at some point became quiet and silent.

It may be because her beauty remains undiminished and shines despite her shameful appearance.

Or perhaps it was the wonder of one warrior who finally emerged victorious after a brutal life-or-death struggle against three warriors of the same level.

Or maybe it's the fear of the cruel hands that slice people apart vertically, but fear was also an expression of respect.

"Next-"

"Stop! Stop this!"

There was a loud shout that cut off Qing's words as she was about to asked for the next oppenent.

"As a military officer, I know it's impolite to interfere in the events of Wulin's heroes! But even if you're not a person of Jianghu, I understand that continuing this life-or-death struggles is wrong! Is this truly the way you Wulin people live?"

It was the commander Wang Ssangryong.

The reason he just watched until now was because Qing had not sent a signal to stop.

That is, it means that the Qing has sent a signal to stop here.

Well, if she said she's tired and exhausted and wanted to stop, it's not going to work out.

Besides, there will definitely be some who would come running looking for an opportunity when she said she's really tired.

So, they had arranged in advance that when Qing signaled by tapping the handle of her sword with her index finger, the commander would stop the duel.

"If it's revenge, you must set a clear goal and stand before the world with pride! Look, you are already in disarray from the blood you've shed, and there's no healthy part of your body. With that miserable state, you are barely standing!"

'She did not avoid those who wanted to ask her about their grudge.'

'Moreover, she stood before the world with confidence, so shouldn't the great men of the world emulate her?'

'So back off now!'

'The land you are standing on was a military base granted by the Emperor. As the master of the Grand General's Office, I will not permit any further battle!'

"General, I am fine."

Qing pretended to stagger and tried to dissuade him.

Then Wang Ssangryong raised his voice even more.

"How could you say you're fine?"

"What you've entangled yourself with, you must untie it yourself. Resolving grudges cannot be set aside just for personal comfort."

Exclamations erupted from all over the place.

Everyone's eyes sparkled because of the amazing spirit of a female warrior that they had just seen with their own eyes and heard with their own ears.

To be exact, they were itching to spread this long tale of bravery to the whole neighborhood, their mouth quivered and their legs trembled.

"Hmph! Revenge was something that should be achieved through one's own strength. The life-or-death struggles you've endured over the day have left you weakened. Then will it not be achieved not due to their own efforts, but to the bravery of the other warriors who already stepped forward to seek revenge?"

'How petty and pathetic was it to try to take revenge by borrowing someone else's power?'

'So, out of respect for the Wulin, I, the general, will not allow you Wulin people to become cowardly any longer!'

\textit{Wow, this general not only has good discipline but also has a sharp tongue.}

If it's ability plus ability, isn't it a true famous general that can be found in history books?

It was a mysterious tongue that even the Qing would admire.

