\chapter{Karma Comes Tumbling Down (6)}

When you say military camp to the Qing, you can't help but think of the military camp in your hometown.

Long, rectangular buildings and overcrowded tenants living together like ants.

And now we get to see a real Ming Dynasty military tent.

What was it? Why was it the same?

Qing was a little embarrassed.

In reality, it seems like a very large military base, with long brick buildings arranged side by side around a large parade ground, except that it's surrounded by a neat wall instead of a barbed wire fence.

Of course, tall buildings are vulnerable to artillery fire, and wooden structures are weak and burn easily, so they are built with stone.

Also, since the military must gather together to exert its power, heating and cooling are military, so you have to endure the evil of military service that you did not choose, and it takes the form that can accommodate the largest number of people per unit of land.

That was the birth of a long, square, two-story brick building.

The only difference was that there was a rather stylish Shandong-style house next to it, perhaps the executives' quarters? It must have been a bit depriving.

Women cannot perform military service.

Even if I want to, I can't.

Not only was it impossible to do, but if caught, it's a serious crime punishable by death, and even the destruction of one's entire family.

This was a national law that arose because there were so many cases of girls dressing up as men and performing military service to avoid sending their male counterparts to do the household chores.

So these poor men are living in a city of twelve hundred people with no women, huddled together like peppers!

Of course, there are ways to escape military service.

You can either pay them to do military service or have a child during your vacation and wait for him to grow up before handing him over.

In any case, the man who proudly crosses a city full of men causes a commotion.

Guys running around with their shirts off for no reason pass by, and I think, "Oh, I think I saw those guys earlier, but did they already turn around and run back?"

When I saw them, they were very sound and excellent soldiers.

Because every soldier you see has a straight posture, a serious expression, and a look of superiority in his eyes, and he was tensing his muscles with his bare upper body.

As we went further, we saw naked men washing themselves along a small, flowing stream.

When you see the blue, you either hide your body in fear or stand proudly with a secret smile.

Oh, my eyes!

It wasn't something to be terrified of seeing men naked again, but it was inevitable that he would suffer serious damage to his eyes and internal injuries.

And finally, in the center, a rather splendid government office appears.

As Qing was heading there, the soldier who had been guiding him spoke to him with difficulty.

"Um, that's not it."

"Oh. I guess I wasn't going straight there."

So, a guest house in a remote corner.

What if Chang was sitting in his seat and sipping the tea he's given?

No matter how long I wait, there was no news.

After waiting for a long time, a man named Pastor Yang appears and asks a question.

(I thought Qing was the pastor's name)

"May I know your name, Your Majesty? And why do you invite the General?"

"General? Ah. Yes. I'd like to see you and speak to you. Did you deliver the message?"

"I'll report to you now, as we follow the reporting system. Um. Did you come alone?"

"yes."

"Any other items or items that will arrive?"

"There isn't any?"

"Well, if there was something you need to tell the General……"

The sheep herd taps the pouch on my waist.

The jingle sound of coins being thrown together.

Of course, Qingdo was now accustomed to the central plains.

I knew what it meant, but I just pretended not to know.

It means that he just stared blankly.

"Is it heavy?"

"No, it's not."

And then, with a look of obvious disappointment, he slumps his shoulders and leaves.

And how many more were there?

"The General says he will not meet you."

"Hmm. Aren't we going to meet? Are you sure? We should be meeting, right?"

Qing smiles, narrowing her eyes.

The two sheep are very kind to him.

"You're saying you refused to meet me even after seeing my hand? Really? I never imagined I'd be treated this coldly."

"Excuse me, please wait a moment!"

Fortunately, Yang Sa-mok was a perceptive person, so after saying that, he left in a rather hasty manner this time.

You were just being sarcastic earlier?

And after a while.

The Shandong Province Commander and General flew in with a bit of exaggeration.

In fact, as soon as he crossed the threshold, he flew up, bang! He hit his knees, put his head down, and clasped his hands together, so it was a really great flying performance.

Even though he was wearing a shiny, shiny armor, he flew halfway and landed on the ground, so he must have learned martial arts to become a commander.

Behind me, the sheep tree's eyes are trembling and its legs are shaking, but the moment Qing looks at it, it collapses to the floor.

Qing felt a chill run down her spine.

This is… … the power of the princess?

I made these people tremble!

I can control these people!

However, the problem was that, unlike the attention seekers with a history of masochistic psychopaths, Qing's feelings are the truth without a single error.

As Qing waves his hand, Yang Sa-mok crawls to the door and hurriedly slams it shut.

"That nobleman……"

"I am Seo Moon-cheong, a disciple of the Shinnyeomun. Your Majesty has given me a badge, but I hope you understand that I cannot reveal the reason for it, as it's a matter of the imperial palace. Without Your Majesty's permission, I cannot reveal it freely."

Mama was actually a general title used to address someone of very high status.

But if the woman who appears with the empress's identity card was Mama, who would that Mama be?

In fact, there are different levels of defeat.

The cards distributed by the royal family also have different types of cards for each person, such as acquaintances, friends, old friends, family members, or benefactors.

But what the woman brought was not something of that rank, but rather the empress's status badge.

The noble person gives me my identification badge.

That is, it means that you should treat this woman as yourself.

It's a bit weird when people say she's a princess.

If people were to collapse and bow their heads like a plague had struck everywhere I went, well, that might be a little fun.

Of course, calling someone your mother or your maid was a very immoral title, but since you've used a trick, it's inevitable that this news will reach the palace. But that's one thing, and this was another.

"You can sit comfortably. I'm the one who came here to make a request."

"Yes, ma'am."

"Madam, you seem too old, um. No."

Qing was about to tell her to just call him Miss Ximen, but then she thought about it and realized that it wouldn't be a good idea for the general.

"I need to get to Hangzhou for some reason, but the evil spirits of the martial arts world are trying to block my path, so I'd like to ask for your escort. Let me see. Where was the Jiangsu Province Commander-in-Chief located?"

"There was no provincial governor's office in Jiangsu Province. However, the central military governor's office was located in Zhuzhou County, Anhui Province."

To put it simply, in the Qing hometown style of organization, the provincial commander was the corps, and the provincial governor's office was the military command.

This man kneeling before the Qing was the commander of Zhongyuan army.

"Curse? How was the name of a city cursed? Um, where was Joo-Hyeon located? What was it?"

"It was about 170 li northwest of Nanjing."

"Hmm. It's not far, but we'll have to take a detour. But it seems like it would be too much trouble for Shandong County to go all the way to Hangzhou…"

At that, Wang Ssangryong's eyes flashed.

To say that you are causing trouble means that you are doing your best to help, and according to the customary law of Zhongyuan, if you receive a favor, you should receive an appropriate reward.

In other words, a crisis was an opportunity!

Perhaps, it could be the lifeline that will take you further up the ladder from the position of commander, which you thought was the end of your official career!

"Your Majesty, you have considered the circumstances of the sword I wield. As a blade forged for this very moment, I dare not even begin to fathom your grace! However, we are always loyal blades under the Emperor, so please, whenever necessary, raise your sword and strike down the enemy!"

"Oh. A loyal subject for eternity."

Mango was the old saying that's written after ten thousand years.

The term "Jungwon Ilman" was also used to mean "all" or "everything," meaning that he was the most loyal subject throughout all of history.

"How could such words be so extravagant! My lord Wang Ssangryong, I am so moved that I dare to shed tears. Would you allow me to weep here?"

"Uh… Please don't make any noise."

"Ugh, ugh……!"

Then, it was Wang Ssangryong who pretended to cry quietly.

The blues continue to be a series of admiration.

What the heck? Is this Zhongyuan' way of flattering?

It's not like it's going to burst, but it has a really classy feel to it.

"For some reason, I must travel through five cities to reach Hangzhou. I live as a martial artist, unable to reveal my other identity. However, this time, there are many Sapa scoundrels targeting me, and I'm overwhelmed, so I'd like to seek military assistance."

However, Qing did not yet know how strong the upward instinct of the officials was.

That means information was leaking out.

Different identity!

Wang Ssangryong's loyalty soared even higher!

"You dare target your majesty!? Give me fifteen days, no, ten! I will use my three thousand cannons to annihilate all the insolent traitors who oppose my majesty!"

"Oh. Three thousand doors."

I have a feeling I'd like to see that.

It wasn't for nothing that the inviolability of official duties arose. If martial artists run wild and commit assassinations, the officials will have no answer, and if angry officials mobilize firearms and soldiers, the martial arts world will also have no answer.

Three thousand gates in just one castle, sixty-three thousand gates in twenty-one military command posts!

That's true mutually assured destruction!

However, in reality, the government was a bit more nervous.

Even though the country has already fallen several times, the martial arts world continues to survive by simply changing the name of the country.

The inviolability of official duties was an excuse for officials who do not want to be associated with the martial arts people, rather than the martial arts people themselves.

"No, the soldiers shouldn't shed blood on this matter. This was my personal karma that I must repay. I simply want to surround myself with soldiers to keep those thugs from attacking."

And then, Qing made a disgustingly contemptuous expression.

I impersonate someone else, get drunk on anonymity, and commit outrageous acts that I can't even bring myself to say, and then get caught and get punished badly, but my expression was that of an innocent victim.

In fact, Qing was really being treated unfairly.

Yun Yuanying was a bad girl. Looking at her evil deeds, she deserves to be impersonated.

How can you do this to me? What did I do wrong?

Why was it wrong to try to make the world's worst bitch into a complete retard?

The Sapha kids are like that too.

If the battle for the Absorbing Magical Arts was over, I will simply accept defeat and go home.

Those little boys are just getting away with it.

Get off me you little shits. What the hell am I doing?

Wang Ssangryong's eyes were moved, not knowing what Qing was thinking.

"How can you, your majesty, speak of personal matters! Your majesty, please refrain from such remarks! Nobility was the mandate of Heaven! What you do, Madam, was the work of the nation!"

"I appreciate that, but innocent blood must not be shed."

"Ugh! How can I ever repay such a kindness! Even to be so considerate of such lowly things? Even if I were struck by lightning and died here, I, Wang Ssangryong, would die smiling!"

For reference, Hahae means a river and the sea, and Chusoo means the grace that the emperor bestows upon the people. If you say that Hahae was like that, it means that it's the greatest heart in the world.

Wang Ssangryong raised his hand in a flash.

"I would like to offer my congratulations to your noble person. I wonder if he was able to live to the age of 1000."

"Oh, maybe? But please don't shout, I have ears to hear."

Then, Wang Ssangryong's loyalty exploded!

It's a thousand years old! At least it's the royal family!

It has been several years since the Emperor, who was already exhausted from hard work, took medicine every day to strengthen his body and meditated to cultivate his mind.

Even management must be respectful in its thinking.

The meaning of having practiced for several years, taking care of one's body with medicinal herbs and meditating, was that the emperor's child was doing nothing but just playing around debaucherously.

Thanks to this, it's now known that the Empress's power was extremely strong.

(Of course, the Empress might be a little aggrieved. Powerful my ass.)

Anyway, if she had a direct connection to the empress and was entrusted with her identity card, she must be from the Imperial family.

How could he missed this opportunity?

It was Wang Ssangryong, who was almost identical to Qing.

This was why they say old officials are scary.

Of course, neither Wang Ssangryong, Qing, Heaven, nor Earth know yet what the outcome of Wang Ssangryong's opportunistic loyalty will be.