\chapter{Karma Comes Tumbling Down (15)}

Originally, joint attack was not an easy task.

Just as blind arrows are dangerous on the battlefield, the blades of comrades fighting alongside you can also fly in from incomprehensible directions and at unexpected times.

Why would the majority have to practice the skill of dealing with the minority by rolling around in a group and learning it as a passing grade?

Not easy.

So, strictly speaking, the combined attack of the three Avengers was not a combined attack, but rather a sequential attack.

Danhwacheol strikes first and grabs the sword, followed by the swordsman, and then Changsu takes advantage of the narrow gap between the three people.

I don't know if they had coordinated beforehand, or if they just got along without any conspiracy.

As always, Danhwacheol's sword tenaciously entangles Qing's trajectory.

It forces the direction of movement of the target's sword to be blocked, and for those skilled at it, the flow was uninterrupted and does not fall like a leech.

This was the technique called the ‘吸' (inhalation) character determination in the martial arts.

Then the swordsman attacks Qing from the right with a wide trajectory.

Even without the weapon, Qing has one hand left, and the transparent flesh of the Soo-Ma-Gong was more than enough to block a sword with his bare hands.

But now you don't have hands?

And there's still Changsu left.

But the weapon called a spear was a straight line drawn to pierce a point or a part.

You can avoid damage with a flexible body.

Up to this point, it was the same development, but would you be fooled by the same method using the same tactics?

This shouldn't be happening.

Rather than rushing to avoid the blade, you should change your position to an advantageous detail.

Qing's head spins around.

The moment Changsu attacks, let go of the entangled sword and swing it around.

It seems that the left hand should deflect the sword diagonally towards the wrist.

If you escape like that, all three enemy weapons will cut through the air, and of course, the gap will follow.

So, from all directions, reading with the Awakening Divine Art, three steps, two steps, one step, and then a wedge!

Where, where are you aiming!

Yeah! Thighs!

The moment when Qing's eyes sparkle!

Qing takes a step back, leans his upper body forward with all his might, releases the strength of his sword, and raises his left arm diagonally.

The tip of the sword soars limply into the sky, and the swordsman's blade flows upward and brushes across the forehead.

Now, if you turn around and get out of here-

That was when.

Suddenly, the blade of Changsu's spear bent like a whip.

The hand that grabbed the center of the spear drew a change, and the straight blade bent and retreated, and instead, the tip of the spear whoosh! Ripped through the air, drawing a fan-like trajectory.

Miss, you can hit me with a spear.

Qing attained great enlightenment.

And in return for enlightenment, ttaak!

A pain that feels like my shins are going to fall off.

The force of the ultimate swordsman's swing with all his might causes his knees to buckle, forcing his feet to bend and his heels to bounce off the back of his thighs.

As my feet rose into the air, I staggered as was natural, and the ground rapidly approached.

Mass transmitted by the flow of air at a moment.

It's exactly like a foot.

Qing grits his teeth and desperately tilts his head back.

A rough kick hits Qing's cheek.

The ball falls out like a kicked ball.

The sky and the earth spin around and around, flying in one piece and landing violently on the back of the head.

The three avengers are hot on their heels.

Three weapons strike down like lightning.

The moment everyone opened their eyes and mouths wide, Qing Shin-hyung counted to eight again.

The weapons of the avengers are ravaging the innocent land.

Qing, who appeared behind me, wiped my cheek with his sleeve.

These kids, kicking a woman in the face?

Even if it's life or death, there's a line.

By the way, whenever he gets the chance, Qing practices soccer with a human head.

You could say that you reap what you sow.

The ball was cold and itchy.

This looks swollen.

The soft mucous membrane of the cheek was torn by the teeth, giving off a strong fishy smell as if it were rusted, and a salty, wet taste lingers on the tongue.

Qing's teeth chattered together.

It's okay, no problem.

Thanks to tilting my head back, my eyes didn't pop out or my ears didn't go deaf, so other than a tear in the inside of my cheek, there weren't any particular problems.

Well, kicking was not a technique used by anyone except a very small number of martial artists.

Just kicking it with brute force.

Even the strength of the bones cannot harm the monstrous body that has already reached the pinnacle of humanity.

If the bullet had lodged in his temple because he hadn't tilted his head back, his eyes would have been damaged by the pressure and his eardrums would have been damaged by the atmospheric pressure. It would have been a shame for the avengers, but what could be done if Qing had escaped?

Because I already learned from experience what happens when you kick someone in the eye.

"Cheer up!" "Wow!" "Wow!"

Cheers, shouts, and boos erupt simultaneously.

However, the goal of the three Avengers was no longer to consider things like magic.

He came out after seeing the soldiers who had been laid down, and his only intention was to kill his enemy and take revenge.

There was no time to spit out the blood that had accumulated in his mouth, so Qing just swallowed it and held his sword against it.

But I learned something else.

Don't arbitrarily predict your opponent's path!

Qing deeply reflected.

At some point, he became so intoxicated with power and victory that he began to view all his enemies as idiots.

I guess I was taking it too lightly because I thought I could easily defeat one of the super climaxes.

Anyone who was unmanned was bound to have at least one life-saving remedy, and they also have at least one method of killing Donggwi Eojin.

Qing clashes with enemies again.

Anyway, there are three weapons, and the rest are just fists anyway, so just hold on with your body.

Even though it was painful enough to kill me, I was able to endure it somehow with my strong body and self-defense skills, as long as I avoided the vital points that I shouldn't have been hit by.

The blue one rolled. It got hit and flew away.

The number of times my life was in danger was just like that when I stepped on the Yeonshin Neungpa Mibo.

So, it seems like the life and death of a blue dragon was constantly being pushed back as it rolls and breaks while flying.

But was that really true?

The enemies are getting more and more cold-hearted.

As the confrontation progressed, the previously awkward combined attacks gradually became more refined, but the Cheonhwa Sword also held out for longer and longer.

Now, even though there are fewer places that haven't been hit, there's not even a hint of discomfort.

So the sense of crisis was rising.

This girl was becoming more and more of a monster!

Rather than a duel where they bicker and strictly forbid touching the face, chest, and local areas, isn't this a life-or-death battle where they aim for each other's lives and spray water?

If they could survive, it would be a huge boost, but if they were to lose, they would be remembered as one of the three fools in the next story of the best female middle school students.

So, you have to kill him.

If you lose, not only will you feel the sorrow of not being able to avenge your enemy, but even your death will remain as a laughing stock for a long time.

So the enemies have now decided to abandon even the minimum dignity that the unmanned people possess.

Qing was thrusting out his approaching fist, using his upper arm muscles, the part of his body called biceps in Qing's hometown, to tighten his grip.

Suddenly, the outstretched fist opens wide. What was this? Why are you putting your hand here?

And then, boom, the sound of cloth being ripped.

Suddenly, a cool breeze blows down my shoulders.

Qing realized what a trick that bastard was doing.

Oh, you want to take off my clothes?

But isn't it true that there are people who communicate with you and people who don't?

What's the big deal about showing some skin when your life was at stake?

Well, it's annoying.

His cheeks were already swollen and blue, and he was rolling around on the floor like it was his own bed, so his uniform was already nothing more than rags.

Now that one shoulder was comfortably bare, the area above it was mottled and bruised, unlike below the elbow where the power of the sorcerer was circulating.

Hmm. I guess I should finish this up and move on to the next ones.

But Qing was rather confident.

Didn't he restrain his immense strength and fight against him with only pure swordsmanship, without even using his Tathagata Goddess?

The enemies who sprinkled dirt and tore clothes looked desperate.

And so, a new combination was born.

Qing holds Danhwacheol's sword in his left hand.

A moment of shock crossed Danhwa-cheol's face.

\textit{Why? I've been parrying your sword-fighting skills with the back of my hand up until now. Didn't you think I could handle it with fore grip?}

Then, the inspector coming from the right suddenly opens his eyes in a panicked manner.

The sharp sword energy, like a crescent moon with both ends tightly closed, split into three branches. The Moonlight Sword also drew the same number of sword shadows, and boom! The three clashes created a single sound of harmony.

Right hand in right hand, left hand in left hand.

Right foot to the right, left foot to the left.

A warrior can exert his power properly only when his limbs are in their proper place.

In the meantime, Changsu takes advantage of the gap.

The moment when the tip of the sword held in Qing's left hand was pointed in that direction, and the single man, who was struggling to pull the sword out of his grip, pushed back and forth with all his might-

now!

The sword, which had regained its freedom at once, was pointed at Chang-nom, and while the two were entangled, Qing stepped on Jin-gak and struck the swordsman.

The moment when Danhwa-cheol and Changsu hastily put away their weapons but are unable to put away their bodies, they collide and fall, tangled together-

Suddenly, the new blue form disappears without a trace.

No, it's not hidden.

Just a sword in the shape of a human.

Qing, holding the sword with both hands, raised her sword towards the sky, towards the midday sun.

Divine Maiden Swordplay, Ximen Surin's Style, Third Movement.

The Great Warrior of Heaven.

The original Divine Maiden Sword's Third Movement imagery was a graceful vertical slash that flowed straight like silky hair.

Since the Master has reinterpreted the path of sword, women too can become great men, and even great men who reach the heavens.

But was the world really like that?

Even after becoming the best in the world, the world was not like that, so contrary to her intentions, she would have been angry at the absurd reality and shouted in anger.

A sword imagery with the screams of a female warrior cut the world apart vertically.

The sword, which had dug in from the shoulder and sliced ​​the ribs vertically, passed through the spearhead, the opposite wrist, the side and the pelvis, and then cut diagonally through the thigh, still had strength left to bury itself deep into the ground.

Several of the old warriors present shuddered as they saw the image of someone in the same position as the Heavenly Blossom Sword.

'Oh, that girl, now that I think about it, she's that Mad Dog's disciple.'

Whether it's the teacher or the student, they're both just as vicious as much of as beautiful. They thought, 'She must have raised a disciple that have the same temper.'

The inspection tower splits in half and collapses.

Qing exhaled.

\textit{Well, Master. Having lived as both, I don't think there's anything wrong with being a woman.}

\textit{If I try, those little bastards with brains in their balls are just going to keep nagging me about taking my clothes off, doing yoga, and having kids?}

But while it was unpleasant and creepy, it was also a huge advantage.

Even in the green forest, she lived as a woman.

Why on earth are you so angry?

The same goes for the White Hands practitioner who learned them.

The White Hands Demonic Art whispered ominously that all men should be killed.

If you entered a demonic possession and become a demon, you'll probably end up listening to those whispers.

\textit{Ah, so this is why demonic possession is called demonic possession. Once possessed, you're just a killing machine, all other thoughts instantly disappearing.}

There's another reason why demonic possession doesn't work.

Cheong wipes the blood off his sword and turns around.Then, the enemy, Lee In-jo, hesitates.

Qing thought for a moment.

\textit{Shit, I almost realized something.}

\textit{Doesn't the image of martial arts come across clearly?}

\textit{But in the end, was it because I just bruteforce it?}

\textit{It's like a sneeze, almost like it's going to come out, but it feels like there's a little bit left, a really little bit left.}

Qing thus makes a decision.

Let's do it one more time!

Qing, stood up straight, in accordance to Ximen Surin's Elegant Woman form, and opened her mouth slightly.

"I said I'd deal with three, but now there are two. So, if anyone here has a grudge against me, feel free to fill in the empty slot."