\chapter{Karma Comes Tumbling Down (2)}

The skin soaked in sweat felt a sensation close to pleasure as it touched the outside air for the first time in a while.

But who will ever feel that?

Yun Yuanying's fingers crossed her neck and touched the back of her chin, and with a gurgle! All the sweat that had been building up poured out, to a degree that could be described as a torrential downpour.

Then the fingers also hesitated.

The fingers on the slender hand that protruded from the front of Qing's chin slowly rubbed against each other, as if measuring the viscosity of the water.

"Oh my. Is this sweat? Oh my god."

"Huh. Nyung-ya? You're going to stop here, right? Ugh, I was a bit mean, but, oh, okay. So you're just kidding, right? I trust you, Nyung-ya. Our Nyung-ya wouldn't do that, would she? Right? Yeah, kid. You're so mean."

Qing tries hard to deny it.

"I told you, didn't I? Is this for you, Miss Ximen? You keep becoming cowardly, so I'm teaching you a big lesson. Well, let's call it discipline."

Is this for me? Discipline?

Qing-i was crying! Anger explodes.

"How was this even for me!? That's all excuses! No, what did I do wrong in the first place? Why are you doing this to me? Is it wrong to try to rid the world of that evil spirit? I was just doing what I had to do? What did I do? What did I do so wrong!?"

I would say it's an impressive scene where such a confident woman suddenly gets angry because someone was showing their face.

The impersonated Yeon-yeong had the right to be angry, but instead, she just smiled faintly.

And so, his fingers, ignoring the beads of sweat dripping down his tattered face, traced their way down to his chin.

"Wait! Wait! Nyung-nim? Ugh, then, besides this, why not some other punishment? What should I do for you? Aside from a public execution that only causes hurt and hatred? Yes, Nyung-nim. I've done bad things in your name, but instead of venting my anger like this, why don't I demand a proper reward that benefits you?"

Qing proposed a negotiation proposal.

Then, Yun Yuanying lets out a laugh that's truly filled with joy.

It's so much fun I could die.

And then the fingers reach the lips in one go!

The cut skin from below hangs down, allowing a refreshing breeze to blow on the lower jaw.

This bitch was serious!

Qing-i leans against Unyeon-yeong, her body drooping.

"Oh my, are you giving up? Already?"

"Fine. I'm going to hide it anyway. It's all wrong now. I don't know how I'm going to carry my face anymore. Yeah, hide it, hide it. It's not like the world will change even if I do that. Even if I do something, the sun will set, the moon will rise, and the world will keep turning. I'm just a small thing…"

It was a case of extreme lethargy and depression.

"Even if you pretend to feel sorry, I won't see it?"

"just-"

"Hehehe."

Finally, bang.

I thought they would all be gone, but the last one was Yun Yuanying, who kicked the inpimyeongu in one go.

Those who were waiting in anticipation for the reveal of the identity of the brain-dead girl were shocked!

Swallowing or exhaling, or strangely enough, completely different actions, can express surprise with the same sound.

The first thought that came to everyone's mind was, why?

Why was there a really brainless, beautiful girl?

Qing was the most powerful beauty in the world.

As time went on, such recognition was spreading.

Except for those who have not yet seen Qing's beauty and think it's an illusion, or those who cannot acknowledge it because of their taste, or their reverence or loyalty to the martial arts world they followed as the best, or the gaze of the most feared wife in the world.

A woman's face drenched in sweat has a certain sensuality that in itself captures a man's gaze.

Especially if it unfolds into the face of the most universally beautiful woman on earth.

"Heavenly Blossom Sword!" "The most beautiful in the world!" "Three heads!" "Three heads? Wasn't it Odu?" "Divine Dragon!" "Why Odu? Do you have four breasts?" "You idiot's butt!" "Ah!" "Ximen Qing!" "Hwajungcheonhwa!"

Eventually, those who find out will come out.

If rumors spread that Qing was popular, wouldn't people be curious to see what kind of face the world's most beautiful woman has?

Pretending not to do anything, he ran out into the street to peek while going for a walk he never went to, going to a tea house he never ate at, and going grocery shopping he never did. Those who saw him couldn't hide their surprise and treated him with the courtesy of a martial artist.

"Heavenly Blossom Sword? Didn't you say you were a disciple of the Shinnyeomun?"

"If you're talking about the Heavenly Flower Sword, isn't that the famous dragon of the Jeongpa faction? That kind of girl learned magic?"

"Wait, what do you mean? Magical arts? The Heavenly Flower Sword learned magic arts? What magic arts?"

"Not just one. From the Soo-Ma-Gong to the Heuk-Sal-Ma-Jang, the Jeon-Mak-Gap, and the Ja-Cha-Ma-Gap. I'm saying you're on the verge of gathering all ten of the greatest magicians in the world?"

"So, you've now got your hands on Saljungsal?"

"Huh?" "Huh?" "Huh?"

Qing looks down at the audience.

Half were shocked, half were dazed.

But, so what? What does that have to do with me?

Qing mutters quietly.

"I should just disappear from this world. I should go somewhere far away, somewhere like the Western Regions, somewhere no one knows, and just continue living the life I couldn't die…"

This process was called the five stages of death in the Qing homeland.

Because it has been revealed to be a universal emotion that appears when an individual was caught up in an event that's beyond their capacity to cope, such as death, great misfortune, or shame, it's also called by another name, the five stages of grief.

This process of denial-anger-bargaining-depression seems to show a kind of decline, a person dying mentally.

But step five.

Paradoxically, the last thing that comes to mind was acceptance!

It was the strength of the person who stood at the end of all this decline.

That was why people, despite the unreasonable violence of nature and the endless hatred between each other, are not broken and ultimately prosper and achieve civilization.

A faint smile appears on Qing's face.

"Hello, everyone. It's me. Ximen-cheong. Hmm. How was it? I'm the super-brained, beautiful girl, right? But I didn't lie, did I?"

All kinds of noises pour out at him.

The place was a chaotic mess, with over a hundred people shouting out their opinions, yet no one could hear what was being said.

"Okay. Okay? Not too dramatic, right?"

Qing turns her head.

Although the Yun Yuanying that was stuck to the back was not visible, on the contrary, the side of Qing's face was clearly visible to Yun Yuanying.

"Oh my. I knew you were beautiful, but this was so. I should have just revealed it. What a waste to show such beauty to those people."

"Saying things that are not even on your mind."

"Haha, that's right. But I was really surprised."

"Hmm. So. Are you letting him go now? If you're going to do it, why not let him go somewhere safer?"

"Oh my. You seem very relaxed."

"What's happened has already happened."

Come to think of it, so what?

Anyway, I don't care what the Sapa guys say.

What are these things that weren't even human in the first place?

What about the master, the Shinnyeomun family, friends, elders, fellow practitioners of the Wulin Alliance, etc.

The shame was that it's not only sold out, but it's also sold out, and even then, I have to keep delivering orders that have been piling up for the rest of my life.

But does that mean?

Magic? Magic was just a trick.

Master said the same thing.

Fraud? If I told you that this was an attempt to eradicate the world of the magic of absorption, who would say anything?

Didn't you learn the magic of absorption?

There are people who can prove that this was all a wicked plot by the Blood Cult, including Master Mo, Lady Mo, and Sword Friend. Changming'er may not be very effective as a witness, but anyway.

"Hmm. Are you letting him go now? Uh, could you maybe take him somewhere safer and let him go? Last time I saw him, he was flying away with all the zombies he'd summoned?"

"Oh, you're just righting the wrongs? The hardship hasn't even begun yet; you're just ready?"

"Huh. I knew it. It's my fault."

Qing snorted.

In the first place, it doesn't make sense to try to defeat or persuade the final boss with vague elements like being in love or something like that.

"Okay. Everyone?"

The audience was still in shock.

They either talk to each other, or they fight each other hard, or they shout something loudly towards each other.

"Miss Ximen? Could you please draw my attention?"

"Should I use the Tathagata Shinjang? Honestly, I feel like giving Nyong a big punch right now. How about just one blow?"

"Oh, my. Hehe. You can do it? But I wouldn't recommend it, would you?"

"Miss. You're saying it doesn't work?"

"Unless you want to know what happens if you try to recklessly use the I-Replacement Method?"

"My internal energy was no joke. I have a ton of it. Even my master said it was practically at the level of a real sage."

"Oh, Miss Ximen, you're amazing. But I'm even more amazing."

As if telling her to do it if she wanted, Yun Yuanying took out the arm that was wrapped around her torso, released her arm, and wrapped it around her waist.

He gave up cleanly.

If it were just the two of us, I'd have seen through the bluff and tried, but with all the bad guys swarming down there, it's a bit much to risk injury.

Besides, if it's greater than Hyeon-gyeong, doesn't that mean it's above her?

It's too much to dismiss as a bluff, because the official status window was the final mastermind.

What did you say? An enemy of humanity? A destroyer of worlds? What kind of nuclear weapon are you?

The blue arm pushes the sky.

At the same time, the career that has been released reveals its presence with a unique sound.

Deeng… … !

The sound of the temple bell suddenly rings out.

The audience was instantly silenced by the clear sound of the wind driving away evil spirits.

"The Tathagata Goddess! The real Heavenly Flower Sword-"

Deeng… … !

The bell rings again as the chattering begins.

If you are unmanned, you know what this action means.

The soldiers quietly look at the coffin.

"Everyone? Lady Ximen here has betrayed my name and brought great shame upon me. She deserves an apology."

Qing grumbled at him.

"Huh. It's all been revealed, so what's the point of an apology? Okay? I'm going to keep selling them, right? If you happen to hear a rumor that in Luoyang, Yeon-yeong stripped naked and danced around, saying, "I sleep with ten men a day, and that's over 9,990, so I'll fill up ten today and make it ten thousand," you'll know it's me. Next time, it won't be the brainless, beautiful girl, but the most beautiful girl in history, Yeon-yeong."

"Oh, then. Could you please contact me before then? I'll take the notoriety, but you have to make sure I can see it."

"joy."

Qing snorted.

However, Yun Yuanying only let out a laugh, as if she was watching a cute child throwing a tantrum.

"Your Majesty the Heavenly Sword must come to Manwolru in Hangzhou, where I am staying, to apologize to me. And along the way, you must stop at five cities: Liu Bang, Lin Gi, Huaiyin, Tai Shui, and Suzhou."

Qing grumbled again.

Actually, there's nothing you can do other than grumble.

"Huh. Why me?"

"Well, if not, I'll turn Lady Ximen's precious people into zombies. Of course, since they're self-reliant zombies, they think for themselves and act with their own will, so they're simply shedding their human nature and becoming zombies. It's not such a bad deal, was it? I don't want to be hated by Lady Ximen. Seriously."

Qing paused.

But, since his words about not wanting to be hated were completely sincere and devoid of humor, I guess I should say that I felt a little relieved.

Because the king of unknown realms can't run wild already.

I don't know what to decorate.

But even if a greater disaster follows later and many people fall into sorrow because of it.

Still, I hope my people are safe.

"If you do it fatally, it will work. If you do it."

"Haha, I knew you would do that."

The expressions on the warriors' faces are not good because they keep whispering to each other and taking pauses along the way.

What if they are not pretty?

"Young Lady Ximen must stay at least four days and three nights in each intermediate city, and must leave the city and arrive at the next within a month. Do you understand what I mean?"

Stop by five cities before heading to Hangzhou.

You must stay in each city for three nights, then leave and arrive at the next city within a month.

In some ways, it was like a travel plan.

However, the journey was revealed to the world.

This will be a once-in-a-lifetime opportunity for those who seek magic.

Those who gather in groups will gather people and come all the way from Hangzhou, so the longer it takes, the more dangerous it will become.

Of course, countless blood vessels will have to be opened.

This was the condition set by Yun Yuanying.

It was a bit of a struggle.
