\chapter{Karma Comes Tumbling Down (10)}

It was a balance of power that Qing had envisioned.

In a life or death battle, the opponent was the best?

One-on-one fights are no longer even considered life or death.

It was not pride, but my own objective level of understanding based on countless experiences.

It was often said that there was no hierarchy in martial arts, and that if you master any martial art deeply, the ultimate goal was the perfection of martial arts.

Just as all streams (萬流) flow and eventually meet in the sea (歸宗) this was exactly what the saying "all streams return to their original form" means.

But was that really true?

No, that's nonsense from the start.

If a rusty iron sword with all its teeth knocked out clashes with a divine sword forged from cloud iron, do we really need to try to see the result?

To begin with, the statement that there was no hierarchy in martial arts hardly qualifies one to say such a thing.

A guy who has mastered the art of magic says something like that?

That kid was talking nonsense about learning new skills.

Is this what a guy who learned third-rate martial arts says?

How does that kid know if there's a difference or not when he's never even used the new skill?

It might sound plausible if someone who learned third-rate martial arts and became a famous master said it.

People are mean and cunning, so they immediately think this way.

Well, that would be true for a talented kid!

So, the new technique was the fastest way to perfection.

I will make ordinary people into geniuses, geniuses into geniuses, and geniuses into immortals.

How many such divine powers does Qing have?

She's such a full-fledged girl that if it doesn't have a purple border, it's not a divine skill, and if it has a gold border, it's worth trying.

There was also ignorant internal energy.

The eight meridians of the qi meridians, which were polished with the reverse-current water-flowing method, were so powerful and energetic that they could literally turn the chamber pot upside down.

Adding the greatest strength of all time to it's truly the icing on the cake, like adding flowers to silk.

Or the icing on the cake.

It was a strong and solid steel elephant with added fire.

In other words, she's a fire-breathing elephant bitch.

Who in the world would defeat such a monster?

So, even if it were a one-on-one life-or-death battle at the highest level, there would be nothing for Qing to gain.

If you destroy one of them in the first place and leave one, it's not a difficult choice between two or one.

So there are three.

Three people would probably be a pretty tricky choice.

And then there's Unrestrained Realm and one-on-one.

To be honest, I'm a little nervous.

But I think that if I have to endure that much, I too can now go beyond the extreme (omitted) and reach the state of Unrestrained Realm.

In fact, I thought that at this level, there would be no real rivals in the martial arts world, but Yun Yuanying, it's written that the destroyer of the world was walking around the world.

If you're the ultimate champion, shouldn't you just quietly wait in the audience room for the challenger to come?

How could it be possible for me to wander around alone and meet someone by chance, and to meet them twice?

Of course, Yun Yuanying may feel wronged.

Can't I go around?

And the second time, I went to see the face because someone was impersonating me, so it wasn't a coincidence.

But Qing was definitely being treated unfairly.

This was not the way to run the world.

And it's urgent.

I need strength.

First, I'll take a picture of the scenery, then I'll go around the cliff wall and finish the Dokgogu sword, and then I'll be able to see the current scenery, right?

You must not wear a mask.

Even if you ignore even a single square of land (which was not something a man would do), you still have to reach the current state to find a gap.

If I were to get into the habit of talking, I honestly think it would be difficult for me to get to the point of being a total idiot.

There, I should stop by Hangzhou and go to the Gaebong Wulin Alliance to ask about the Jiangshi.

Doesn't Yun Yuanying know too much about that guy?

Even if she was the eldest daughter of the Jinju family, who are famous for their jiangshi, how can she know the feelings of a jiangshi?

Wow, you know Nyenyeong very well. Are you a resident?

Of course, there may not be any correct information.

Because Kang Si-sul was a vision of a certain place.

It's like asking the Wulin Alliance about the poison of the Tang family.

But if we're on the same side, I guess I can give you some advice.

While Qing was lost in thought, the warriors were unable to come to their senses due to the commotion and declaration that they should rush in if they were attacked.

"A super climax set? One on one with Hwa-kyung?"

"No, what the hell are you talking about?"

Those who hear this are simply dumbfounded.

When many attack one, it's a vile joint attack! And when a master attacks a weaker player, wouldn't they be criticized for it being a vile act?

And under the strict laws of Zhongyuan, it means that you can take revenge on those who commit mean deeds without any worries.

If you win like that, what will be the aftereffects?

The revenge of the best girl in the middle school was second to none.

The enraged Wulin Alliance will declare the Murim public enemy and immediately issue a notice of execution upon discovery.

And was that the right thing to do if you just bring in the military right away?

What kind of life or death decision was this, with the soldiers who were on my side behind me?

If you're in a hurry, do you intervene, and if you win, do you fire artillery in retaliation?

Unfortunately, while this matchup was fair to the Qing, for the Muin, it was fucking, fucking hell.

So, there was no one who hesitates and asks for a life or death decision.

All the way until Qing woke up from her long thoughts.

What? Aren't you going to attack?

Well then? I guess I should go.

"It seems no one wants to challenge me to a showdown. Well then, I'll take my leave. General, shall we go now?"

"Hmm. Let's move!"

The drones are once again at a loss.

No, you said we happened to be going the same route?

What do you mean, 'Shall we go?' Aren't you saying you're going together?

As the flag flutters and the soldiers confidently approach the castle gate, the warriors who had been blocking the way spread out to the left and right to clear the way.

It's absurd, but I don't want to touch the moving trap that will make my legs fly away if I touch it.

But, in the gap between the two sides, wouldn't one unmanned person be sitting there in a cool pose?

A familiar face in Qingdo, Dokgo-geom, now not Dokgo-geom Jongjeongpil.

Manjeoksal Widaemyeong pretended to know.

"No, Jongjeong, since when have you been here?"

"It was there from the beginning."

"No, if you're here, you should say hello first. How can a younger sibling just ignore their older brother? Jongjeong, that's not how you should conduct yourself. Even if it's not your older brother, if you see someone you know, you should approach them first, say hello, and ask how they're doing. Even if fate was fleeting, in the end, all that remains was fate. So, you should date a little, too. How old are you, and why are you still single?"

"Hmm."

Jongjeongpil was trying hard to keep the mood calm.

But Qing didn't miss the way the corners of Jongjeongpil's eyes trembled.

"People can't live alone. You need a companion, a home to return to, a family to call your own, and then you can steadily improve your martial arts skills. You're always so reserved, so just keep your mouth shut and act like it doesn't matter. Okay, right now, like that. Don't be like that. Well, maybe I should arrange a dinner for you sometime next month. First, you need to meet a woman. Whether it's eye contact, soul mate, love, or children."

It was a torrent of naggings.

No, that old man, he was a nice, polite middle-aged man who spoke to me politely earlier, but now he's suddenly meddling like a neighborhood aunt?

Of course, there were people like that.

He's a cool guy who's polite when he doesn't know what he's doing.

A person who, once you become close to them, cannot tolerate 'well-intentioned advice' because of their endless meddling and nagging.

"Even now, look. No, you, when on earth did you get those clothes? No, let's see. Weren't they the same ones I saw at the performance last year? Man, even if substance was more important than appearance, it's still the same. Just as a dish with the same taste was more appealing when it's adorned with extravagant decorations, you need to dress up a bit to attract women. If you walk around like a half-beggar, even the women you're trying to please will be completely disgusted…"

Qing seemed to know why Jongjeongpil pretend to not know Widae-myeong.

I think even I would want to pretend not to know.

I think that perhaps Manjeoksal Daehyeop was someone who doesn't get recognized no matter where he goes.

A somehow compassionate gaze from Qing.

Jongjeongpil, who noticed him, looked at Qing with his characteristically indifferent expression.

It was a look that seemed to be mixed with some kind of sympathy or appeal.

"Ahem. Grand Master Wei, I understand you are particularly concerned about your brother, whom you haven't seen in a long time, but I wonder if Grand Master Jongjeong has some business with me and isn't staying behind?"

"Oh, you're right. I seem to have acted rashly again. Awkward, maybe next time, or maybe later, we can have dinner together. I'm saying this out of consideration for you, so don't dismiss it as nagging."

It's a perfect ending to the nagging.

In this way, Jongjeongpil, who was liberated, nods his head slightly to Qing again to express his gratitude.

And then he opened his mouth but paused for a moment.

And then he looks at Qing with a somewhat sad look in his eyes.

"I originally wanted to ask Heavenly Blossom Sword about his true intentions regarding the Manmin Alliance, but upon thinking about it, I realized it wasn't a light topic to discuss in such a chaotic setting."

Qing tilted her head.

What was Manmin Gongryun?

Everyone practices together?

"So, I would like to ask about the development and further perfection of the entire martial arts community through the common ownership of martial arts and the justice of the world. Would you like to join me for a moment and have a serious conversation?"

No, why was this guy so red?

By the way, it was somehow sad.

It seemed like he wanted to avoid dinner.

Qing was wondering what to do for a moment.

Shouldn't we stop this before a real communist was born?

If you think about it, it's the seed I sowed, so I have to take care of it.

"Okay, do that."

Jongjeongpil nodded, giving a nod of thanks, and walked over to sit next to Qing.

The problem was that Qing was riding a magnificent white horse, and the general horse named Baekro was proudly holding its head high and showing off its style.

So, Jongjeongpil, who was standing next to him, ended up looking like a servant who had to hold the reins.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had subdued the spirit of the first Heavenly Horse, the Cheonmahon, and as a superior, he could take it out and summon it at will.

The so-called Qing's most famous trick, the last drinking party trick that has not yet been shown to his friends, was the secret technique, the Heavenly Horse Summoning.

By the way, I haven't used it to liven up a drinking party yet because I was punished so badly when I showed it to Ximensurin.

And Wang Ssangryong, as a commander, had similar types of summoning techniques and ultimate techniques.

Summon the manager by that name!

However, this could be said to be a much more rigorous study than summoning the Qing Heavenly Horse.

Qing has to be summoned directly to retrieve the Cheonma Soul, but the Doji Commander can just enter the village and it will automatically activate, and the officials will come to visit with gifts.

Just like the workers who come to mine minerals in the Qing bloodline, a traditional Korean game and an old electronic game.

So, as soon as we arrived at the reserve military facility, the fortress garrison, which existed in every city, there was a fat guy who warmly welcomed the group.

"Oh my, Commander! I am so delighted that you have come this far! Since you are a general busy with national affairs, isn't this truly a great blessing for the royal family, a loyal subject of all time?"

A loyal and capable general was a blessing to the country simply by his presence, as he establishes military command and also prevents the enemy from approaching.

That's exactly what the fat guy means.

"Ahem."

Wang Ssangryong coughed in vain.

In normal times, I would laugh heartily and say, "Haha, I'm the great general!" and praise myself.

Imperial Family, at this point, Wang Ssangryong became a little, no, a lot uncomfortable.

You little punk, what do you think I am if you say something like that when your mom was right next to you!

At that, the fat man's eyes tremble.

What the heck? Did I do something wrong?

A landowner was a very high-ranking official who rules over a large city and its surrounding areas.

Of course, compared to the city commander who oversees the military of the entire Shandong Province, he was just a weak commoner.

So, I have no choice but to be cautious.

"Wow. General. You're truly respected! I knew you'd be so capable because your soldiers are so elite."

At that, Wang Ssangryong's expression brightened like the sun.

"No, no, what are you talking about, Io? That's too much praise."

Wang Ssangryong was barely able to suppress his natural politeness because there was a stranger (Jong Jeongpil) in his seat.

The landlord also immediately noticed this subtle relationship.

The landlord was a commoner compared to the governor, but to this extent, our ancestors have been landlords for generations, and we can boast that our family was a family of landlords, a very, very high position.

And the high-ranking officials of the current imperial family are basically very perceptive and have the amazing ability to grasp the hierarchical relationship at a glance.

This was the so-called manager's eye, or new eye.

"Hehe, thank you for your hard work on the way here! I've prepared a small banquet to offer my sincere gratitude for your hard work. Please come and grace the occasion with your presence."

Even though his body and gaze were directed at Wang Ssangryong, Qing somehow felt as if he was speaking to me.

This was the fear of management!

They possess strange abilities that cannot be explained by common sense in Zhongyuan or by modern science in their homeland!

For example, these non-directional communications, the spirit workers who exist in the register but have no substance yet receive a salary, the forgiveness of the sins of the guilty, the accumulation of wealth that has no source but springs from somewhere, etc.

"Ahem, a drinking table during a mission-"

Gulp. The sound of Qing swallowing his saliva.

"Oh, I'm thirsty! Can a man's thirst be quenched with water? My Lord, I will gratefully accept it!"

It was a general who suddenly felt thirsty.

How loud can the sound of swallowing saliva be?

Although small and weak, she was big and mighty to Wang Ssangryong.

This was the mysterious power of management.

Wang Ssangryong will probably remember this conversation for a long time.

\textit{Madame likes alcohol. Make a note on that.}

Like this, first day in Weifang started.
