\chapter{Karma Comes Tumbling Down (5)}

Jiaozhou, Shandong Province.

The Chinese characters are different from the Jiaozhou region mentioned in the Romance of the Three Kingdoms, which was the current Jiaozhou region, which was called Yangguang, including Guangdong and Guangxi.

The name of the inland sea that formed a deep indentation in the peninsula that made the silent poem so prosperous was Gyoju Bay.

Looking at the terrain alone, Gyoju City was in a much more advantageous position for trade than Jeomuk City, which has to turn right upon entering the bay.

The city of Gyoju was convenient for ships to dock because the water level was low and the ships do not have to break. Above all, it's close to the central plains, so it's advantageous for trade.

But in reality, not only was there no trade, but there are no fishing boats even around the area.

Why was that?

This was because Jiaozhou was a military garrison of a provincial city where the provincial commander's office of Shandong Province was located.

Whether or not some grand feast was held in Mount Lao, the soldiers continue to focus on their original mission, shedding blood, sweat, and tears.

However, you may be wondering what exactly the military's mission is, what exactly our job is.

What on earth are the soldiers doing, each stuck in their respective positions?

Even if the bandits are on the rise, we don't know.

Even if the Japanese invaders are on the rise, we don't know.

It's not like there's a war going on, so we're not fighting against it.

Does the military train diligently with the military spirit that the best defense was the best defense?

That's not it either.

So what was the original mission of the military?

Farming!

Farming was the foundation of the world and the great foundation of the world, and it's also a major task that makes a country exist.

"Oh, today was tough. I'm going to fall behind."

"Have you heard, Yeon Gun-chong? I heard that the martial artists are wielding swords in Mount Lao."

A commander was a position that commands fifty people.

Under the white tiger commanding one hundred men, firearms are divided equally, and under him are five small guards commanding ten men.

So, the total number of Baekhoso members was 113.

It's vague, so roughly 120 people in the organization.

"Those kids are just eating and using knives. What's so amazing about that?"

"The greatest divine power in the world has appeared."

"What does it have to do with us being the best in the world and being the best? We just have to work hard at what we have to do. Fuck, I don't want to do this. I fucking don't want to do this."

"They say there was the most beautiful woman in the world-"

"Please report this in detail."

Military interests have always been the same in every world, so this can also be said to be an instinct inherent in humanity.

It was a woman's instinct to become hungry when she enters the military.

"That's it. The world's best divine art has appeared in Mount Lao-"

"Hey, Sam So-gi, let's start with the most beautiful woman in the world. How pretty was she to be the most beautiful woman in the world?"

Then, the three sogis of Baekhoso in Dorin River clear their throats.

The smoke gun thing was a bit annoying, but this kid was trying to text me that he's from Gangnam, and he's bragging about being a ink eater. What the heck.

But I'm curious so I'll hold back.

"Ahem. Then, to be called the most beautiful in the world, shouldn't there be some absolute beauty standard and how well one fits that definition? First, one should have hair as glossy as a crow's eye, flowing like a waterfall without any tangles. One should also have lips the color of an apricot, soft but not thick, with a full lower lip and a sparkling upper lip. One's teeth should be dazzlingly white, flawless, and without any gaps or ridges, right?"

The gunman gulped at him.

"Also, the chest should be as white as a snow-covered valley, the eyebrows should be graceful, like drawing a distant mountain, and the gaze, don't you know? It's that look in your eyes, that slight turn of the head as if looking or not, meeting your pupils, but that moist, appealing look that seems to be on the verge of tears…."

"Wow, shit, this was driving me crazy. And? And?"

Lee Eo-ga generously reveals the beauty she has always harbored inside.

"When you look at the eyes, the pupils should be slightly covered by the upper and lower eyelids, and there should be two or three moons shining brightly, and the white part should be completely transparent without even a single blood vessel, let alone a single stain."

"Wow, shit, this was really gross. You should write a book about this. You could write a book about it. Why did you join the military? If you wrote a book about that, all the men in the world would come running to you with their gold coins."

"Huh? Is that so? Should I sell my military records?"

"Anyway, and then? And again?"

Lee Eo-ga generously reveals the beauty he had always harbored.

When we say someone was from Gangnam, we usually mean someone from the Suzhou and Hangzhou areas, and Suzhou and Hangzhou are the largest entertainment cities in Central China.

And the thing that the literati of Gangnam did was to sing songs of elegance while having fun with women, and now it was fashionable for them to compete with each other in sensuality, saying that their own concept of beauty was the ultimate beauty.

So, the beauty view of this intellectual from Gangnam must be quite stimulating to a country bumpkin from Shandong.

Before anyone knew it, soldiers had swarmed around the small space, gulping and perking their ears, all listening intently with serious expressions on their faces so as not to miss a single word.

It was during this time that Zhongyuan-style novels and views on beauties were being released one after another.

"And also, her waist was as thin as an ant, and her body was slender and thin, so she was not tall but still slender-"

"Wait a minute. That's not it. Even if the waist was thin, shouldn't the chest and butt be large?"

The smoke gun was causing trouble.

"Then isn't that too frivolous and obscene? Isn't such an extreme curve the kind of vulgarity only prostitutes would do?"

"This was the problem, you bastards who are fed up with ink. What do you mean, vulgar? If you cover your face with cheap makeup and make it look obscene, you're vulgar, even if you're thin. And was your body shape really what determines your mood? If you're full from top to bottom, but your waist was perfectly slender, that's the best."

"A woman with such a nature can never appear innocent or pure. Her very body was obscene, so isn't it somehow filthy?"

"Oh my. Our ancestors also liked women with big breasts and butts, oh my."

"The ancestors of that ancestor said that a slim woman was the best."

In fact, the image of a beauty in Zhongyuan ranged from a completely skinny woman in the Jin, Wei, Jin, Southern and Northern Dynasties to a very voluptuous woman in the Sui, Tang, and Ten Kingdoms Dynasties.

And nowadays, the general consensus was that shape was more important than size, although it should be large enough to make the waist stand out.

Then it was noisy.

"After all, a woman was all about her breasts! That's motherly love!"

"This was a kid who'll get fucked by a sow. Do you get offended by cows? It's all an illusion, you know."

"Well, I have small breasts-"

"Shut up!" "Shut up!"

A war of words breaks out between the plump and moderate factions.

A few small-minded people just glance around and shrug their shoulders.

Today, after the autumn harvest, it was a peaceful day for the soldiers.

Up to here.

That was until a woman suddenly appeared, falling from the sky.

"Huh! A fairy! It's a fairy!"

"Ugh." "Ugh!" "Ugh! Th-that!"

What was it? Why am I so surprised?

Is this your first time seeing a martial artist?

Qing tilted his head.

Then the soldiers' reaction was that they were even more out of breath and about to faint.

"Oh. Sorry to startle you. Are you soldiers from the Shandong Provincial Command? I'm on my way there. Could you tell me the direction?"

With an apologetic expression, his eyebrows formed a sharp angle, and beneath them, his slightly squinted eyes, small black pupils, held the wisdom characteristic of Taoism.

The soldiers had completely forgotten how to breathe.

Ah, Fairy. That was the beauty of the celestial world.

This was not a beauty that can exist in the human world.

I hope they are fresh. Fresh people are bastards.

Among the soldiers who were completely dumbfounded, the commander, Yeon Gun, opened his mouth.

Suddenly appearing and asking about the location of the military tents was an extremely heinous act that reveals military secrets and disregards national law!

So the firearm answered him.

"Yes, that, that, that way……"

"Ah! Thank you! Then!"

Qing smiles brightly and expresses his gratitude.

A peerless smile that's more splendid than any flower in the world, yet also blooms brightly like a child.

The soldiers all had the same experience at that moment.

My heart pounded, I rolled on the floor, and bang bang bang! It was an experience where I overdid myself and the blood vessels in my body felt like they were going to burst in time with the beat.

Qing-i Ta-dak, the weightless walk of the Wolnyeo Sanbo, flies gracefully towards the commander.

Then, the soldiers who were left in their seats were left alone.

Somehow, the remaining scent seemed fragrant, sob, sob, only the sound of heavy breathing lingered.

"Yeon Gun-chong, I, I was wrong. A woman's waist should be as slender as an ant, but her breasts and buttocks should be as magnificent as Mount Tai, so that her clothes will burst open with a scream. A slender waist, fair skin, and enormous breasts and buttocks—the bigger the better! This, this was the ultimate beauty, the way of the celestial world."

He continues to mutter.

"I must sell my military records. I must write a book about what I saw and make it widely known. This was my given mission."

He continued to clench his fist.

If Qing was a person well-versed in the history of Zhongyuan literature, the name Yi Yi would have brought to mind one of the greatest writers of Zhongyuan classics.

In the first place, who would be curious about the history of Zhongyuan literature?

So, it can be said that the possibility of Qing being like that would never happen even if the world were repeated a hundred million times.

Qing knows how much the officials of Zhongyuan care about their outward appearance.

Because the Confucian scholar taught us.

Even after experiencing it, you have to tell me so that I can understand, because Qing originally has no thoughts!

Tian Yuxue was the one who stopped and hid Qing, who was about to run to the commander's office, and then immediately bought him silk clothes, flower sandals, and gold-leafed jewel decorations and gave them to him.

If you go on like that, you're not a precious guest, you're just a raider.

So, the sight of Qing, who had been all dolled up, was truly brain dead, possessing the destructive power to stop a man's brain.

"Is Commander Nari inside? Hmm? Excuse me? Are you listening to me?"

She waved her delicate, white, slender fingers in front of the soldiers.

But the guards are unresponsive.

Hmm? What? Did he die standing up?

Then, a gasp of relief comes out.

Even if the brain stops, one must still breathe, but if one reaches a state of transcendent brain death, rather than just brain death, one can make a person forget even to breathe.

The story of the brainless girl was the clear truth without any lies.

After having eleven children and filling the small group with eleven children, the young man was able to rest peacefully among his grown children, and the remaining wife wiped away her tears, saying, "Don't be too sad."

The soldier who came to his senses asked urgently.

"What business does your Majesty have for you……"

"Okay, this. Could you please give this to Commander Nari and tell her that a guest has arrived?"

"yes?"

He reluctantly accepts what the soldier offers him, but was startled when he sees what it's.

Of course, a single soldier would not dare to recognize the empress's identity badge.

But even at first glance, it was obvious that it was not an ordinary item, and that was something a military man should naturally have.

"Huh. Yes! I will follow your orders! Chung!"

The commander of the Dohwisa Temple, who had even given a vigorous salute to an outsider, ran forward with all his might.

The commander-in-chief was the commander in chief of the military in the provincial capital.

Of course, this does not mean that all the military of the provincial governor are gathered in one place, and the provincial commander, called Su-eo, commands approximately 1,200 soldiers under the direct jurisdiction of the provincial commander.

And four thousand hoshos are placed near the commander's office so that they can be pulled out and used immediately when needed.

So, even in peacetime, the commander was a powerful person who can constantly mobilize six thousand soldiers from five thousand garrisons.

So, what was the power of the commander?

Shandong Province's provincial commander Wang Shuanglong was tossing and turning in boredom on the huge bed in his room, which was a neatly built palace-like mansion, even though it was called a military tent.

Usually, when he was bored, he was Wang Ssangryong, who carried out the mission of strengthening the country and training (manipulating, harassing) the soldiers.

But even that wasn't possible at a time like harvest time, because farming was still a very important matter.

So I'm bored, I'm bored.

The kids were lying around messily these days because they were busy with the harvest, but Wang Ssangryong was debating whether or not to have them do a thorough cleaning of the barracks today.

-General, are you there?

As if he had discovered the commander's evil plan, Pastor Yang knocked on the door.

A pastor was a servant who takes care of miscellaneous tasks in a military camp.

"Huh? Why?"

-Excuse me, a guest came to visit, and he left his identification card with me. I've never seen him before…

"Really? How about the gift?"

When we say gift, we mean a polite gift, or bribe.

But if you say it's a bribe, it's too negative.

It refers to the basic signs of surname that should be taken care of according to the customary law of Zhongyuan.

In particular, the higher the level of the person you want to meet, the more the level of basic sincerity increases.

And the commander was one of the most powerful men in Zhongyuan.

If you count down the hierarchy of power from the Emperor, the fingers are in a row, and the commander was roughly at the tip of the toes.

If you were to show up and ask for a meeting without an appointment, you would need to bring at least a few carts or enough gold for two men to carry.

-You said you just came here in person?

"What? Do you think the commander was some low-level local official? How dare you come here just for show? Send me back."

-Yes, I will do that.

Wang Ssangryong snorted with excitement.

Although Wang Ssangryong was a fairly honest man for a commander, the lack of gifts was not a matter of gain, but rather a matter of face.

Even if you look down on people, how can you come here with bare hands and try to see people?

I didn't think the other person was precious.

If it's a procession of a noble person, it's natural for them to have a large procession, so they absolutely can't show up alone.

But? There was no such thing as absolute in this world.

After a while, Pastor Yang speaks again.

-Excuse me, the guest asked why she was being treated so rudely even after giving the plaque. She said it was most unusual treatment. What should I do?

"Huh? Really? Who the hell does she think she is? Let's go and take a look at that plaque."

The two guards politely opened the door and held out the tablets they had carefully presented in both hands.

Wang Ssangryong looked at it with a displeased expression and then-

"Gah!"

"General?"

"B-bring her in now! What are you doing! Bring her now! No, no! Where is she!? Y-yes, I would have politely invited her to the highest-class guest room!? Go and tell her that I was too busy with work to check, so if she stay a moment, I will personally greet her!"

"Yes?"

Then Wang Ssangryong shouted.

"Do you want to see us all die? Hurry up!!"
