\chapter{Karma Comes Tumbling Down (4)}

Unrestrained Realm was a bit like that.

If you let your guard down, they won't do anything, whether it's a surprise attack or poison.

Even if this body was so transcendent and supreme, what can you do if you fight it head-on?

The body was light and the mind was clear.

This was because the Taoist and Buddhist energies that had been silent for a while were now spreading their wings all at once.

Taoist priest Ximen-cheong appears!

Complete liberation from the Tao!

As the pure energy melted into the four limbs, the spirit that had been erecting thorns settled down gently.

The sunset-colored river, which has been cold for a long time, greets Qing with a bright smile.

And soon, the sword begins to dance.

When you look at the sword, there was no person, and when you look at the person, there was no sword. The two are one and cannot be seen separately. This was the unity of the sword and the mind.

The innocent sword dance of the moon girl swinging a tree branch among the monkeys, a natural dance without any form or ceremony, just flowing as it comes.

The swordsmanship itself was so exciting and thrilling, and so enjoyable that even the sensation of the killing in my hands becomes distant.

Every once in a while, a majestic bell rings.

Jungwon bastard! Ximen Qing! Heavenly Blossom Sword! The voices of the various masters approach Qing, threatening to kill him, and Qing scatters and disappears without a trace.

The more obstacles a Nungpa Mibo has to avoid, the more burdensome it becomes, and the biggest obstacle among them was people.

Thanks to that, a sharp pain like a needle being stuck in my brain suddenly strikes me.

But that too was only for a moment, as the pure energy of the Great Master of the Pure Land wrapped around his head and stroked it, calming him down.

"Are you running away again? Come here! Come here and fight proudly!"

Qing laughs.

A master of Unrestrained Realm was holding on to his peak and was telling him not to run away but to fight proudly?

Of course, the super-clever Ximen-cheong was a person of the highest level.

Other people's anger was my pleasure, isn't it?

Qing's eyes are as longing as a crescent moon.

Thanks to this, the hand that throws the sword becomes excited.

Moon Girl Sword, the second chapter.

No child playing with monkeys

An innocent child plays with a monkey.

Long, long ago, a very long time ago.

A girl who grew up alone in the mountains meets a group of monkeys.

The moment when Wolnyeo first met someone other than me.

Although they had similar appearances, they were monkeys who could not communicate with each other, so they got along through sword fighting rather than conversation.

The moment when the sword that had been swinging alone in the air until now finally collides with someone.

The blue sword dance gradually takes shape.

It's not like a child drawing crookedly in the air, but it clearly shows the cleverness of someone who recognizes their opponent and was determined to hit them.

Thus, the Qing dance was no longer a solo dance, but was reborn as a dance performed in harmony.

When you clash swords and the enemy pushes you, you are pushed back and spin around, and when you meet eyes with the opponent who has changed and clash weapons, the hem of your clothes flows gently.

The reason why fighting was a deeper form of love than dancing was because it digs deeper into the other person than a simple skin-to-skin dance.

As the blue blade pierces the enemy's heart.

The first and third seconds of the Moon Lady Sword (Jin) are actually not that different.

Faster. More intensely. More powerfully. More gently.

But this was precisely what martial arts seek.

Something more powerful.

The third chapter of the Moon Lady Sword.

A young child in trouble

The world was on fire with the phone, but the world of the child in blue, the moon girl, was just nature, still peaceful, like a separate island.

And the moon girl grows up.

No longer a child, her limbs have grown thin, and her swollen chest was a lump of flesh that's uncomfortable and shakes painfully, making her cry.

Still, I like my increased height, longer arms, and increased muscle strength.

Although Wolnyeo has become a woman, she was still just a child in blue clothes in the peaceful forest.

Yesterday, today, and tomorrow, Wolnyeo will just hang out with the monkeys, swinging branches and laughing innocently.

Suddenly, Wolnyeo looks around.

On a vast expanse of land that seems familiar.

The forest where they used to play has gone, and a snow-covered field has spread out before them, but Wolnyeo's eyes are only sparkling with curiosity.

Because there was no fear in the four characters of innocence and purity.

Within, Wolnyeo, Qing-i, blinks her eyes.

If we put down fine snow instead of blood, and if we put up a pure white ice rink instead of a wall of blood, this would be the town that the star with the mouth looked down on.

Instead of the ugly stars boiling with mercury in the sky, there were only fluttering snowflakes endlessly above.

Why was it a snowy field?

Because, it's a path that hasn't been taken yet.

The realm where my heart colors the world, the beginning of thought, my thoughts are still uncharted territory, a pure snowy field that only I can walk.

Qing looked at the ice wall and immediately realized.

Ah. This was still a little lacking. What a pity.

Qing immediately turns his back and takes in the vast, endless snowy field behind him.

A wide, open land, a single line of footprints that stretches on without end.

Qing smiles with relief.

But we've come this far, haven't we?

Yeah, what's with the mouth?

Why did I keep obsessing over the mouth?

Strength was necessary, but if you are already addicted to swordsmanship and are also influenced by martial arts, you will become a true great demon, yes, a great man.

But even so, it's not the Ximen Qing of Daeman, right?

I've achieved the union of the new sword and the harmony of the flower was just around the corner.

The little blues that clap their hands, embrace each other, and circle around in joy in the blue's dantian are the true spirits of Taoism and Buddhism.

Because it was a moment when a new strategy that the threshold for slaughter would gradually rise and eventually become dull was effective.

Qing exhales with clear eyes.

On the floor, there are unmanned people groaning and groaning.

It was so surprising that this many people are left alive after the Qing's rampage.

When Qing looked around, the unmanned people flinched and retreated.

Qing looked up in the direction of the wide-open entrance to the Shingazimyo Shrine, or rather, above it, and nodded.

Well then, let's go for a bit.

The new Ximen Qing was divided into eight parts.

Among them, a translucent blue bird spreads its arms wide and flies up, completing an elegant flight before touching the ground and running with brisk steps.

"The Heavenly Sword was running away!" "Catch it!"

Only then did the seekers of the magic absorption technique respond with a shout, as if they had suddenly come to their senses.

At once, their eyes were filled with a fierce, murderous energy and their pupils were clouded with desire.

But the blue had already reached the wide open space in front of the stone gate.

"Haha, I'm going to the breasts! If you can, come and follow me!"

Qing shouts and quickly jumps into the bushes, disappearing without a trace.

The unmanned people rushing towards him.

However, since more than half of those who remained in the vacant lot were there, each of them made a rational decision.

Now that I have seen with my own eyes the Neungpa Mibo that I had only heard of, I can say that no matter how hard I search for it in the mountains, it will be in vain.

But next city? Breast?

How was the city named Yubang?

What city was founded by Han Gaozu?

Since we're going to enter Yubanghyeon anyway, whether we set up camp in front of it or inside the city, if we wait, they'll come anyway.

Those who are rushing down the mountain path are probably those who have reported to the temple or gathered people they know to wait for the Cheonhwa Sword somewhere first.

So, the pursuers also slow down with tired expressions at the sight of Qing quickly receding.

Trees sway to the left and right of the blue sky.

Qing's lightness was unparalleled in the world.

The movement of turning left and right like lightning and running forward was enough to prove that it deserves to be called that.

A single sound penetrated Qing's ears as he ran.

-Hey, was that all you're going to do if you just run away? What are you going to do now?

-Oh! Master! What about the kids!?

Qing's face brightened.

When I turned my head, a figure running parallel to the blue appeared between the trees.

-For now, he's hiding up there. Can't you tone down that damned voice? Is that a transmission? He's shouting in one direction.

-Thank goodness! I'm running so it's hard!

A sound was produced only when it reaches the other person.

It was difficult to hit the opponent when he moves, so it's equally difficult to convey the message.

Of course, even when not running, he was a confident young man who couldn't control his voice.

Qing looked around,

-Master!? I'm from the Wulin Alliance! I went in to eliminate the Absorbing Demonic Arts! I fell into the Blood Cult's trap and was falsely accused of learning all kinds of demonic arts! Could you please tell me that!?

It was the source of Qing's confidence.

Those Sapa guys? Those ronin? Who would believe those guys who came here to find the magic anyway?

If you look at Yun Yuanying, she was also quite innocent.

Wouldn't it be okay if you insist that it's not magic?

He was a Qing who followed the teachings of Ximensurin very faithfully.

Incitement and fabrication are still fragments of a future that's too early for the people of Zhongyuan.

-Is it a false accusation? Well, I guess it depends on how you use magic.

I saw my disciple, Tian Yuxue, wielding his magic sword directly from the audience through the glass.

But does that mean the disciple was evil?

What kind of evil mind would make eye contact and then flash a bright smile and show off sparkling affection?

It was clear that he was a disciple with a cruel and murderous nature, but I had never seen his violence directed at anyone other than the wicked, and I was certain that it had always been that way.

-Ah! Master! By any chance! Do you still have the Mount Lao map!? Can you give it to me!?

-Turn slightly to the left. Let's see from the front.

Two people running fast are gradually closing the distance between themselves by adjusting their angles.

Not long after, Tian Yuxue, who was disguised next to me, held out a map.

"Oh, Master. But if the Wulin Alliance calls for a rescue team or something, please stop them. They'll end up in a dogfight. Just leave them alone and they'll figure it out, so don't worry."

"Huh? How? You're going to do whatever that pesky bitch tells you to do, aren't you? How did you manage to make it all the way to Hangzhou by yourself?"

"You've got an idea, right? Where was that map you borrowed? Where should I go?"

"You mean the commander's barracks? Why there? Oh! I heard you have connections in the military?"

Tian Yuxue's expression was bright and cheerful.

No matter how much one treats the government as if it were nothing, the constables and soldiers are fundamentally different and are the property of the emperor.

Qing laughs and nods at him.

It wasn't for nothing that Qing asked Yun Yuanying if she could get help.

Come all the way to Hangzhou?

Okay, then I'll go.

But do you think I'll go in with a bit of a hardship and bloody shit just like that?

No, I'll go in comfortably and confidently.

Didn't they say that official duties are inviolable?

Even if that weren't the case, I wonder if there's any unmanned unit that would want to properly fight with the military.

Because if you open it, shells will rain down.

Anyway, eventually I'll have to go to the palace over there.

You can't just keep putting it off forever, right?
