\chapter{Karma Comes Tumbling Down (9)}

Qing was confident.

A witch who has gathered four of the ten greatest magicians in the world?

No. Five was mastered and one was registered.

Since she had collected six, technically speaking, Qing could not have been the world's greatest witch who had collected four of the world's ten greatest magicians.

If I had to say, maybe the greatest witch in the world?

"I'll explain everything one by one! First, there's a suspicion that I learned the White Hand Demonic Art, but that's not true. The technique I learned was called Divine Maiden's Divine Hands, and at first glance, they might seem similar."

The unmanned people looked at him and wondered what kind of strange thing this was.

"This was a peerless craft created by my teacher, Godmother Ximen Surin. Did you know that Shinnyeomun was famous for its fairy craft? It's a beauty and self-defense technique that cultivates beautiful hands!"

Qing spreads out her hands.

A gasp of "Oh" erupted from his young men, but they soon shut their mouths tightly as a look of caution urging them to be more careful.

Because the love of the hands of the people of Zhongyuan was special.

But it's really pretty.

Because the skin was white, the fingers were slender and long, and the wrinkles at the joints were faint, the hands were as elegant as if they had been carved from white jade (marble).

Anyway, everyone has a suspicious look on their face.

But no one really shouted or started a fight.

Whether the relationship between the priests was good or bad, he sold his master in front of the people because if he refuted it, it could lead to bloody revenge, even life or death.

For reference, according to the customary law of Zhongyuan, the teacher and the student are one body, and attacking the teacher was the same as attacking the student.

(On the contrary, the converse does not hold)

And above all, there was the biggest reason.

Ximen Surin, the absolute best female martial artist known in the martial arts world, was too scary.

So, when it comes to the Divine Maiden's Divine Hand, whether it's true or false, it must be true.

So, although the warriors did not refute, their gaze towards Qing was extremely crooked.

There are still three magic spells left, so they look like they are waiting to hear what they have to say.

"Next, was it Black Hand Slaying Palm? At that time, the black hand wasn't the mark Black Hand Slaying Palm's, but just a glove on this hand."

"Huh?" "What!?" "What?"

The unmanned vehicles expressed surprise.

This was unbelievable! The identity of the black hand was a black glove. What an unexpected truth!

"Does that make sense!"

The warrior who had been shouting about magic and witches earlier was picking on me again this time.

But Qing was calm.

"Does that even make sense? Isn't the black hand of the Black Hand Slaying Palm an unavoidable side effect of it? How can your hands turn black and white all the time? And on top of that, you have the White Hand Demonic Art in your right hand and the Black Hand Slaying Palm in your left? What kind of Demonic Art can you learn half and half to achieve that?"

"Ahem." "Uh-huh." "That's true."

People nodded.

Come to think of it, the White Hands Demonic Art was a beautiful, indestructible white hand, while the Black Hand Slaying Palm was a hideous, indestructible black hand.

Then the two should be mixed to make it gray, or the realm should be tilted towards the higher side, what's half and half?

If you only learn the basics halfway, will it be like that?

"Normally if someone has black hands, you'd assume they wore a black cloth. If someone claimed I have mastered the Black Hand Slaying Palm, shouldn't we be suspicious of their wicked intentions from the beginning?"

Then Manjeoksal Widamyeong asks.

"What wicked intentions?"

"'That girl was a bad girl because she's mastered Demonic Arts. She's even worse because she's mastered multiple types of Demonic Arts. So, you can catch her and take away her martial arts by any means necessary'. What do you think?"

Widae-myeong nodded.

In the first place, Weidae-myeong didn't come here to find the Demonic Arts.

The rumors said she was a wicked witch who had mastered all kinds of evil magic and was trying to dye the world in blood. But she was also known as a swordsman of Orthodox sect, so he just wanted to find out the truth about her.

What if that's true?

I will cut down that ugly hypocrite.

"I saw it with my own eyes! That bitch brandished that black hand and went against my agenda, you little brat, ugh, that bitch smashed my little brother's head!"

But people's gaze was cold.

He was a man of resentment, saying that his brother was murdered.

There was ample motivation to commit a slander.

"Okay. And next, was that a Purple Lightning Demonic Art? Hmm, honestly, I don't get it. Everyone? You all know what a Purple Lightning Demonic Art is, right?"

Purple lightning that reacts to emotions.

The reason why the Purple Lightning Demonic Art was so vicious was because the mere movement of the practitioner's moods caused the true energy to react and the lightning to strike first.

In the words of the Qing homeland, this was an anger management disorder that causes extremely lethal attacks.

"I am widely known to the world as the Thousand Flower Sword, and my appearance and actions are widely known, so where was it ever rumored that I could breathe lightning?"

The unmanned personnel are making a lot of noise.

When I heard it, it was true again.

If Qing was a real Purple Lightning Demonic Art witch, she should have been struck lightning and thunder whenever she got even the slightest bit angry.

But? There's no such rumor, right?

Qing had erased three out of four rumors.

The unmanned vehicles look at the blue sky with a long gaze.

There was still one left.

"And lastly. It's called the Chakra Demonic Tribulation. Why on earth would that be? Hmm."

Qing pretends to think.

Just like that for a while.

Qing, who was taking a break, clapped his hands.

"Oh, maybe it's because my eyes sparkle so much? It's a bit embarrassing to say it myself, but honestly, aren't my eyes big and beautiful?"

The point was that the eyes were so bright that they looked like the front wheels of a wheel-wheeled demon.

He draws three valleys between the eyebrows of all the warriors, and in the letters he draws the character for "river" (川).

Of course, it's beautiful because it's black and white, glossy, large, and moist.

Even so, that's a bit…

And do you usually say things like that with your own mouth?

Just as Qing easily put the super-brained, beautiful girl in her mouth, people also took the super-brained, beautiful girl half as a joke.

But what if you say it's not pretty?

It's so pretty that it's even more absurd.

"Who do you think was a cripple? There are already many people who have witnessed this, not just me! Isn't that right!?"

"That's right! I too have clearly seen the cursed eyes drawn by the three soul flames!"

"I saw it too!" "Me too!"

It seems that the logic that I must have seen something wrong because my eyes were too bright was too far-fetched.

The unmanned personnel present at the scene strongly argued that they had not seen anything wrong.

but?

The tongue of the Qing was an intangible, unbreakable realm recognized by the Supreme Master of the Tang family.

Would he have taken such a desperate measure because he had nothing to say?

"Uh, you guys? Uh, I'm twenty-one this year, right? I won the Rising Dragon Compettition with my family's Yue Maiden Swordplay, and I had chance encounter with the Tathagata's Divine Palm, the immortal art of Shaolin. From my master, I learned the Zhu's Heart Cleansing Mirror, the Divine Maiden Cultivation, the Divine Maiden Sword, and the Divine Maiden Footwork. And I'm also currently practicing the Qinggong methods of the Thousand Li Flight and the Subtle Wave Treading Steps."

Suddenly the atmosphere was one of self-praise.

Amidst the expressions of the unmanned soldiers, the bait that Qing had developed explodes.

"If you don't learn martial arts from the inside out, how can you possibly learn more martial arts here?"

The expressions on the unmanned people's faces.

If you personify an exclamation mark, it would be like this.

Come to think of it, the Heavenly Blossom Sword in front of me was just twenty-one years old, a young and immature member of the Orthodox sect.

"Does it make sense that the Orthodox sect's Rising Dragon learned Demonic Art in the first place?"

"I already have a ton of Divine Arts, so why bother learning Demonic Arts and becoming a public enemy?"

"Huh. Stupid things. I never believed those rumors in the first place. They were probably just an excuse to steal your martial arts skills."

Manjeoksal Widamyeong now had an apologetic expression on his face.

He was a swordsman who has killed only the Japanese pirates and has a blue number on his head.

"As I grow older, I become more and more suspicious. I made a grave mistake. I apologize to the Heavenly Blossom Sword."

The triangle in Qing's heart, now almost oval, worn away, its rotten, stinking conscience working for the first time in a long while, stabbing at his insides.

\textit{Well, I feel a little sorry for this old man… … .}

Even those in the stone chamber thought, "Hmm, what did I see wrong?"

Could it be that the bicycle rider was not aiming for the Cheonhwa Sword, but rather was aiming for the Cheonhwa Sword on the spot?

The black hand could have been a sword.

The eyes were so big and clear that they looked like irises?

Well, it's a bit of a blow to my pride, but it's really big and clear, so maybe that's possible?

"No! I saw it!"

Of course, not everyone was convinced or doubted themselves, so a few who felt wronged continued to run around claiming that the woman was a witch who had mastered magic.

And then-

"Yeah! Corpses in that stone chamber! You bitch! Ha, why didn't I think of that? You were the only one in the stone chamber, and how can we explain all those corpses with punctured hearts! When we entered the innermost part of the Shingajjimyo, it was full of corpses that had been tortured! That bitch has mastered the Heart Absorption, the Heart Absorption!"

People's eyes are focused on Qing.

Qing has a pitiful look in her eyes.

"What kind of idiot in the world would learn something like the Heart Absorption while mastering the Taoist divine art?"

Then the unmanned people also had the same look in their eyes.

That's right. Who would master the ancient Taoist art awaken the purity of the dantian and then scatter it with the practice of the Heart Absorption?

The method of training and the means of raising the level afterward are extremely vicious, and it's a mundane art that's far from pure internal energy from the beginning.

The man who lost his agenda was now left with only evil and shouting loudly.

"Then what about the magic of absorption!? There were some Moknaei there!"

"That's why I told you it was a trap of the Blood Cult."

"That's just your claim! You have no evidence!"

"So, you say that I mastered the Heart Absorption in the stone chamber in just a few hours, and used it to make a group of people lose their lives?"

Absorption magic was a very vicious magic that allows victory in one-on-one situations, almost ignoring the difference in skill level.

But what about many-to-one?

Absorbing the source one at a time.

And the suction mine that's sucking the source was vulnerable, so the fact that there are multiple throats in the first place was a big mistake.

"Anyway, it's because of you! You…!"

Finally, the unruly man who had lost his agenda began to act recklessly without any basis or basis.

These arguments are not meant to convince each other.

If your feelings are hurt in the first place, how can you communicate?

Since the argument was intended to win over the onlookers, it's very obvious to anyone who sees who was being unreasonable.

"That bitch was the witch! That bitch is-"

Deeng!

At that moment, Qing rings the temple bell.

Those who have already heard it are amazed at how the Buddhist temple bell sounds no matter how many times they hear it, and those who are hearing it for the first time are thrilled by the legendary miracle they have only heard about.

"Even if everything was a conspiracy by the Blood Cult, isn't it true that those who wield a sword are not free from karma? Such are the laws of the martial arts world, so those seeking revenge should seek a life-or-death match. Don't act like a girl, just talking nonsense."

Don't act like a girl and just talk nonsense.

It was the voice of a woman who had been talking so hard until now.

But it's okay because Qing was really a woman.

"And the same goes for those who still think I have acquired the Heart Absorption, and those who want to acquire Demonic Arts through that."

Qing smiles coldly.

"Oh, that's right. Since my martial arts are so advanced, I can deal with up to three Transcendent Realm Masters at once, and one Unrestrained Realm Master one-on-one."

It was Qing's second attempt.

Qing recalled that vast snowfield, that majestic ice wall that was just a little bit too far away to reach.

We need a proper fight.

What do you call this fight where you constantly rack your brain for tricks, curse, give medicine, talk nonsense, and make others lose their minds, and use all kinds of means, including poison, to create an opening and aim for it, without regard for the means or method?

Oh, right!

Other than the clever way.

If someone were to hear my true intentions, they would say that it's not clever, but rather mean, dirty, and deadly.

Well anyway.

Isn't it time to move beyond the extremes of transcendence, transcendence, and transcendence and look to the next realm?