\chapter{Karma Comes Tumbling Down (7)}

Under the commanding officer, there are two comrades. (For some reason, it's not the one who seems like he'd be standing up.)

If I were to speak in the style of the Ximen Qing, I would say he would be a deputy commander.

And under the commander, there are four commanders.

They are (omitted) operational staff members.

The city commander makes the final decision on all of the city commander's work, meaning he only stamps his seal.

The working-level commanding officers and the dispatched officers each have different responsibilities.

Comrade Do Ji-hui was in charge of military training and field work.

The commanding officer was responsible for patrols, weapons, supplies, cooperation, etc., and also for the military camps.

The field was the work of all six practitioners.

Because farming, or the military's first duty, was farming.

That's how important it's.

So, what would the six practitioners think of the person with the decision-making authority?

He looked at me like I was crazy.

"No, are you crazy? What kind of operation was this during the harvest season?"

"That's right, General. To go on a campaign at the end of the year's farming?"

"It's a bit strange to be called a martial artist's bodyguard. Of course, if it's not the harvest season, you can think of it as just a training session."

The fact that I don't like the way the martial artist escorts me was always a secondary issue.

Even if he was not a martial artist but a beggar, if he had received a decent amount of gold and silver, the army would have moved. What are you saying was that you are accepting anything during this busy farming season?

"What's the problem? Shouldn't we allocate two hundred men from each of the four corners, and have the Su-eo Army fill two hundred men, and then deploy a thousand? Wouldn't it be enough for four to do the work of five, with just a little more effort?"

It was a sound that would enrage the four people listening.

Especially those who have worked on group projects in their hometown of Qing or at university can understand the outrage to some extent.

Even simple childish morals like working together to achieve the same results are not observed.

If Mr. Hong Mo-gwi, who shook the world with his beard, red hair, and standing posture, had tried group projects, he would have understood how absurd the dream of communism is, and instead of writing a book, he would have opened a hairy bossam restaurant.

"Isn't it a matter of possibility? Why on earth should we head to Hangzhou at this time?"

"And even if we leave as soon as tomorrow, how can military affairs work like that? Supply isn't something you just pack up and head out on the road. And if you get hungry along the way, it's even less of a chore to just go buy some food and eat."

That's ridiculous.

Don't you know it's Thanksgiving today?

They were subordinates who shouted, "Absolutely protect the harvest and protect farming."

Then Wang Ssangryong answered.

"Really? Then I guess I can just proceed with the sign language?"

A garrison was a unit of 1,200 men under the direct command of a commander.

Then, Comrade Do Ji-Hui-Dong, Comrade Seong Wang-Qing, and Comrade Seong quickly met eyes with Comrade Do Ji-Hui-Dong, Comrade Yo Ram-In, who was standing next to him.

These days, there are rumors that even the approvals are stamped by the two pastors, so the two people who hold the real power as practitioners exchanged glances.

"Why was this kid so hard-working? He's not the type of kid to work this hard."

"There's definitely something going on here. Look at that. The corners of his lips are twitching. He's straining to keep from smiling."

'I was excited because he said he was doing it alone on purpose, but it's suspicious. It's really suspicious.'

If there was one serious problem with the current administration, it's the serious backlog of personnel.

Backlog means that it's so full that it's blocked and cannot pass through. Since the law basically states that public officials hold office for life and there was no retirement age, it's a phenomenon that has become worse as the country's history progresses.

So, the two of them, who have been stuck in ambiguous high-ranking positions for over fifteen years, get along very well.

So the meeting was disrupted, and then the two of them sneaked into the general's quarters.

"Sir, let me be honest. Isn't this a problem?"

"I have been giving my all to the Lord, but have you ever heard the saying among the young people these days, ‘a hunting dog that only catches rabbits without food will boil its master'?"

It may seem rude, but it's something we say because we're close.

In the first place, weren't all the adjutant positions in Zhongyuan people who were brought up and installed in their positions by the owners of that relationship (Gwansi)?

"Ahem. You guys. I too remained silent because of a strict order. If you guys just stand there and oppose me, what will become of me?"

It means there was something.

Then the two people become brighter.

"As expected!" "I believed in you!"

"Ahem. That martial artist, ahem, was a very, very, very close lady to the master of the West Palace."

And then the two people's eyes lit up!

And at this military conference, the two comrades exchanged words as if they had switched people.

"I thought about it, and no matter how urgent the farming work may be, the military's duty was to be strong and self-reliant, so I think it would be our loyalty to show our gratitude for this kindness through mobile training."

"I'm sure the General has his own thoughts. I've been elevated to the rank of comrade by your grace, so I'm truly ashamed to have dared to speak out against you."

This was Comrade Yo, who proudly said that he had entered the country through the general's connections.

However, in the common sense of Zhongyuan, it's not at all shameful to have secured a position through connections to the powerful. Rather, it's a great source of pride that should be boasted about to the whole world.

In the Qing homeland, it can also be said to be a unique custom of Zhongyuan people.

This was how the preparations for the so-called precious mama escort operation proceeded.

Since the commander was a gathering of five thousand garrison commanders, he first selects two hundred soldiers from each thousand garrison commander to participate in the march to Hangzhou.

How would the soldiers feel if they were suddenly ordered to march out of the blue?

In the evening, a white tiger cub runs to gather the children and shouts with a bright smile,

"We're marching! We've decided to march! I've personally stepped forward and secured the marching spot!"

Baekho was roughly a company commander in the Qing hometown unit.

The company commander gathered all the company members together and bragged about how he had done a march that he didn't have to do, and that he had barely managed to send our company on a march, using all his meager strength.

So what was the reaction of the company members?

"Wow! As expected from Baekho-nim!" "He's the best!" "I love you, Baekho-nim!" "I respect you!"

The white tiger cub rises to become the white tiger.

From today on, this White Tiger was my sole commander, and anyone who opposes this White Tiger was opposing me. (It should have been so.)

The Korean people will not be able to understand.

Why are these crazy people cheering and jumping up and down in joy at having to march?

At a time when you should be running around like crazy?

but.

It was now harvest season, harvest operation in progress.

It was a gigantic labor force equivalent to serious construction work, where one bends down all day to cut rice, and then raises and lowers the upper body on one side, making very violent movements to break the rice.

And the central people are originally good at walking.

Unlike the weak civilized people of this era, the primitive people of ancient times were still so immature that they had the barbaric idea of ​​basically walking on two feet wherever they went.

Do you want to harvest or do you want to march in battle gear?

No, where the hell was the idiot who picks the harvest?

So, the white tigers fought and pleaded with each other to go on a march, and even exchanged gold and silver.

It's even said that there's a plan to invite a fairy!

The most beautiful woman in the world, Heavenly Blossom Sword Ximen Qing.

There were quite a few soldiers who heard that rumor, but not all of them believed it.

But now, armed with a faith stronger than anyone else's, they were soldiers ready to punish with their fists anyone who dared to insult the solemn beauty of the most beautiful woman in the world.

But instead of the annoying grains of rice, you can walk around and look at the fairy's jade eyes?

Is this truly a luxury that can exist in reality? Or was it just a dream?

It was precious news that filled me with fear, thinking, "This was not a happiness that a soldier should be able to enjoy."

So, we prepared to march in a hurry.

In fact, those who set out on the march had no particular reason to be busy.

The remaining military staff members, such as the Taoist sergeants, the privates, and the deputy sergeants, who suddenly had to take charge of the supply line, were the only ones who felt like they were going to die. Those who were going on a march just had to pack their bags, leave the barracks, and eat the food they got from the rations that came.

Thus, the thousand soldiers who had finished preparing to march were lined up neatly and ready to go out.

Standing on the high platform in front of him, as a VIP, Qing felt so sorry that he almost died.

Aren't you going on a march that'sn't even in your destiny because of me?

I wonder if I'm causing too much trouble for something I'm doing for fun.

However, there was one curious thing.

Everyone seems to have a bright smile on their face, their eyes bright and shining with enthusiasm.

What kind of look do you have on your face while marching?

Isn't it like a cow going to the slaughterhouse?

Was this country's military this strong?

It was a realization of the military's power and why the martial arts world didn't dare to tamper with the government. (No)

From the commander of the Kyojuhyeon Dojihwisa Temple to the Yubanghyeon area, there was no obstruction along the way, it's an open plain.

Originally, the military camps of Zhongyuan were stationed by building walls in the middle of the plains.

Because the military's primary job was farming.

Although Mercury was at a greater disadvantage than the mountainous region, it's possible to quickly deploy troops in all directions.

Moreover, if you ignore it and pass by, self-sufficient soldiers will come out and hit you in the back of the head, so it has the secondary advantage of becoming a kind of obstacle that you must pass by after capturing it.

So, the three hundred ri march to Yubanghyeon.

Since I'm not in a hurry to meet your majesty, I plan to travel exactly 100 li per day.

For a person from Zhongyuan, walking about 100 li a day would be considered a moderate amount of walking, so from the soldiers' perspective, no, really, how can there be such a sweet thing in the world? It's so sweet, it's really so sweet!

The morale of the soldiers was also high, so they must be busy keeping a close eye on all sides.

Actually, it's not a border, but I'm just craning my neck to see if the fairy was passing by.

The fact that he doesn't know the circumstances was simply admirable.

I wonder if this general who was good at flattery was a great figure who can be found in a search in his hometown, or if he was a great general in the Shih Dynasty civilization.

A useful way to live.

This was about the cunning heart of man.

It was the worst of the worst to show a bad attitude when someone orders you to do something.

Rather, I feel bad that the person who ordered me to do it's the one who was taking advantage of me.

Pretending to be hard was a serious responsibility.

The other person will feel sorry.

The best way to do this was to show enthusiasm.

Only then will you be thankful!

So, thank you very much, Qing.

You've been through a lot because of me…

By the way, there are some best books among the best books.

It's about working hard, but pretending not to be able to do it and ruining the job.

Because if you do a good job, you will continue to be exploited.

Qing rides a white horse and rustles.

It was a truly attractive white warhorse with a slender body and well-defined muscles.

Is this… …real?

Then what about the king's palace that's living a full life, eating and playing at the Seolga store?

I guess he's not talking?

No matter how you look at it, it looks like the general's personal horse.

I wonder if I can ride this.

"What are you saying! A warhorse was heaven's property. How can I claim it as mine? And look at the eyes of this white heron. Wouldn't even Inseok be thrilled to serve you? Isn't that why even dumb animals are amazed by your noble demeanor?"

Should I say that to the owner?

The white horse, named Baekro, also turned its sad eyes toward Qing.

I'm not going to ride it?

Horses are extremely intelligent animals, and warhorses in particular are trained to be sensitive to power.

Only then will the subordinates follow the leader's horse and charge into the enemy lines.

So, the captain's horse, which was carrying the general, decided to change masters as soon as it saw his master's attitude toward Qing.

"Oh, ma'am! Please use this saddle! This was a new product from Heukcheon Horse Gear, and it's a precious item that absorbs the shock from your body!"

For your information, Heukcheon Magu was a luxury brand that produces all kinds of saddlery in Zhongyuan.

Rumor has it that they even supply it to the royal family.

It was also a disguised business of the Cheonmasin Church, which devotes itself to riding pleasure day and night while crossing deserts and wilderness.

Comrade Sung! Where did you go last night? You even went to buy instant noodles! Tell me something!

'Huh. Opportunity comes when you grab it.'

This principle continues the aggressive actions of the three commanders who want to look good to the mother.

The burdensome Qing slowly slowed down his speech, and then, after a while, the burdensome invasion of aggressive attacks began again.

So, the soldiers who went forward and backward on the march and saw the face of the fairy were filled with happiness.

The white heron, walking proudly with its head held high, was thrilling and enjoyable to watch the gazes looking up at me.

So, forward, forward.

When Qing was on horseback, snacks and drinks are served, and when he was away from the three commanders, the soldiers who shout "Fairy Lady" politely offer their snacks.

No, you have to give them snacks in moderation. Who would eat snacks all day long?

Yeah, I don't know, but I eat all day.

Yum, this was delicious.

Even during a short break, it's a burden, a burden, a burden to set up a tent and offer a makeshift bed.

What the heck? Are you trying to drive me out by making me feel like a burden?

And every time we eat, where on earth do they get the food in this vast wasteland?

Yum. But it's delicious… … .

But this somehow feels similar to when I was at Seolga Sanghoe or Taecheong Sangbang.

Hmm. I want to see Grandpa.

Our pretty Seol Ga-ryeon needs fake breasts made too.

Three days like that.

And so, Weifang! Finally Weifang!

A county with a name like a certain Emperor\footnote{In the original text, Weifang was written as 유방/ Yubang, which sounds similar to Liu Bang, the first Han's dynasty emperor} appears before your eyes.
