\chapter{Karma Comes Tumbling Down (3)}

Qing was speechless.

What the heck? You said you didn't want to be hated, but now you're saying, "If you can survive, try to survive." Isn't that something like that?

"Couldn't you give me something I can do? I clearly said a little while ago, but don't you know what "little" means?"

"Oh my. Would it be so difficult for the owner of the Nengpa Mibo to get rid of me? You don't have to come all the way to Hangzhou, do you? Even if someone becomes a zombie, it's just a change of form. The name. The personality. The memories. The appearance. They all remain the same."

Yun Yuanying never said she would kill him.

He just said he would turn his precious person into a zombie.

The name, personality, memories, and appearance are all the same.

A self-reliant spirit that acts of its own will.

But was that really true?

And why was that a threat?

"Can you think and act for yourself? Then what's the difference between humans and zombies?"

"Oh my. Miss Ximen? Humans and zombies don't resemble each other even in the slightest. They may seem similar, but the two can never coexist."

"Why? You said they're just like humans? And even the river you fall into has a human mutation?"

"Oh, really? Hehe, Miss Ximen. Do you know what the first thought that comes to mind when you become a zombie is? Ah, I'm no longer human. I certainly have a human appearance, the same consciousness, the same soul, but they can never accept me as human."

"Why? They're exactly the same as humans, so why? Are you saying they're mentally different? You said they were the same just now?"

"Well, because jiangshi don't age? Think about it. They're all the same, but they're like humans who don't age. Wouldn't jiangshi actually be even more exceptional? Then, would the current rulers of this world, the humans, be able to accept that?"

"Hmm. Are you a resident by any chance? Do you know me well?"

"Hehe, I've always heard that sentiment. You know what I do, right? Oh, right. If you really don't like it, Lady Ximen could become a zombie."

In that moment, Qing's alertness suddenly soared.

Qing frowns.

"Yes. That's right. Is this all because of my constitution? Isn't that why I'm so clingy right now?"

"Yes. Did you know?"

Qing-i snorts.

"I don't stop people who like me, but I don't like people who only like me for my body. If my body was all they care about, then what's the difference between that and a pervert or a traitor?"

"You still don't understand, Miss Ximen. What you mean to me. Miss Ximen was more precious to me than anything else in the world."

"Are you telling me to kill someone precious to you?"

"Hehe. It's okay. I'd prefer to become a zombie while still alive, but I'm fine with being dead, too. So, Lady Ximen, don't worry. When you're dead, oh my goodness, I'll be right there before your eyes."

"Miss, I'm going to go."

The body was the goal, so it doesn't matter whether it's alive or dead.

What the heck was this? Is this crazy?

Of course, that doesn't mean that he will just become a zombie, nor does he have any intention of offering up any of his precious people as zombies.

Because it's suspicious.

Nothing changes, and all I can do was realize that this body was a zombie, not a human, and that my species has changed.

What does it mean to not age? Is it immortality? Or eternal life?

"Okay. I don't have to go through this alone, right? It's okay to get help, right?"

"Oh my? Miss Ximen? Are you willing to share this perilous journey with someone? Really? The Miss Ximen I know is, well, of course, if you wish, you may."

I thought you would try to solve it on your own anyway.

That was the answer that came back.

"You clearly said it was okay? Can't you change your mind later?"

"Okay. Okay. Promise."

The soft skin that touches my cheek.

Miss, everyone was watching.

Qing frowned.

"Well then, I'll wait in Hangzhou. Hehe, it's been so long since I've waited for someone. My heart's already pounding. Yes, it's been so long since waiting felt like hope…"

At the same time, a hand was touching my back.

No, just send it nicely. Why don't you just push it?

Qing lands lightly on the floor and rolls her eyes in disbelief.

It was Yeon-yeong who had been stuck behind me the whole time and whose face I could not see.

My heart skipped a beat the moment I saw it, ma'am. Why?

The face, sculpted to Qing's taste, was right there.

However, Qing quickly came to his senses.

Wow! Bad karma! Hmm. Bad karma. This was making me realize something.

When I came to my senses, I could see my shortcomings.

Nyenyeong, your heart was truly simple.

If only my breasts were bigger, I'd be completely out of my mind. Bigger was better, after all. Hmm. Hmm.

Of course, it's natural that a super pretty girl with a weak constitution cannot have big breasts.

Then it looks sturdy.

Yi-mei, I miss you.

It's mine, I can do whatever I want with it.

Yun Yuanying's expression becomes subtle.

Something, something seems off, and perhaps she has a vague sense of a very rude intention, as if she were a woman.

"Okay, everyone. I'll be taking my leave now."

As the coffin door suddenly opens, Yun Yuanying lies face down.

As Yun Yuanying fell into the coffin, the little zombies that looked like they had seen before began to lift the four legs attached to the coffin.

What should I call this?

A palanquin? A hearse? A hearse?

The eight-legged palanquin, driven by a sign, soars high into the sky as if it were powered by some kind of propulsion system, cutting through the air.

The coffin disappears in an instant.

And in that place, there were the explorers of the new power who were hesitantly looking around, and the world's most beautiful woman who had taken off her mask and revealed her true identity.

-Master. Is there a reason you have to go through all this trouble?

Suddenly, a voice knocked on Yun Yuanying's ear.

In response, Yun Yuanying gently curled the corners of her lips inside the closed coffin.

"Hehe, Miss Ximen will come to realize just how shallow and fragile human emotions truly are. When you despair at the prospect of the relationships you've cherished so far being turned to a knife, you'll remember that there was always someone who waited for you, unwaveringly."

No matter how strong the relationship, even blood relations, human greed was ultimately directed solely at oneself.

Kindness was like the sun, the more you look towards it with hope, the higher it flies and gets closer.

But the sun was an illusion, in reality it lies far away, in a void more cruel than any other in this world, and it deceives.

So, those who fly high end up falling for a long time.

Because that's the way the world was as seen by Yun Yuanying.

-As expected of the master! A super brain-killing beauty! Oh, you like this, right? Can I use it?

"Haha. Of course."

-But what if, by any chance, the Jeongpa unmanned forces move to rescue him?

"Is that your excuse for the Blood Cult members? That a major war will break out. Well, it doesn't really matter, but for now, we have to adjust to their rhythm, right? Even if we discard them when it's time, they're still useful."

If, by any chance, a large-scale movement were to be made to rescue Qing, wouldn't it be obvious that a war between the two factions would break out?

Even though she pretends to be tough on the outside, will Ximen, who was soft-hearted, be able to endure the price of blood?

Even if Ximen Sojo can endure, can the people of the world do the same?

When you face such a torrent of resentment and hatred, you will realize that human order was trivial and futile.

As if the new blue form was shaking, it split into eight translucent blue forms and ran off in different directions.

Neungpa Mibo.

It was an unprecedented, peerless technique that ensured the safety of my body.

Now, it's the Ximen-cheong and Doro-cheong, so there's no need to hide anything, right?

A dizzying fall, a unique sense of dizziness as if falling in all directions, and the world unfolding in a twisted and crumpled state, a man was looking at Qing with surprised eyes.

Three hundred points of bad karma. The afterlife? Only three hundred points?

Looking at Yun Yuanying's evil deeds, I think 300 points was a bit cute.

By the way, was this kid wearing a martial arts uniform from the Choryubukducheon?

The reason why Qing remembers the Sapa's military uniform was because they were the ones who massacred the villagers and set up a stronghold in the mountains.

Yeah. Death penalty.

Qing's palm touches the man's chest.

Deeng! The Sapha unmanned building collapses with its eyes wide open, accompanied by the sound of a bell.

Qing pulled out the Moonlight Sword after a long time.

Even if you don't know about Yun Yuanying, Ximen Qing uses a sword.

"From now on, I will kill all those who attack me, considering it a matter of life and death!"

Even though it's a gathering of bad guys, if you're looking for the world's most evil magician, you're all probably ready to risk your life.

The Qing was again divided into eight.

In a situation where enemies are spread out all around, the annoying restriction of the Nungpa Mibo appearing with his back to the enemy actually becomes an advantage.

However, perhaps because of the high density of people, the spatial leap of the Nungpa Mibo's shrinking technique also seemed to place a great burden on the path setting.

A terrible headache comes over me, as if a long needle was stabbing my brain.

People staring at the beauty of the most beautiful woman in the world who entered the crowd with surprised eyes.

Those pretty lips draw a curve.

The blue sword spreads out like a fan.

Cha Jang-chang, several weapons were thrown away, and with a bang, a sword was torn in half and flew.

The rascal holding the remaining part looks at the broken bottle and the green onion alternately.

This kid can't even use a sword properly, so why did he crawl in here looking for some magic?

Pook, Qing pierces his heart, making him pay for his recklessness, then runs away and stabs him again with a fierce blow.

A heavy feel. A single, knotted shape.

The sword must come out in a different direction from where it entered.

It was a personal preference, but when dealing with a large number of people like this, cruelty becomes a great weapon.

Qing swings his sword with all his might, his spirits still undiminished.

When a knife was stuck in your body, you unconsciously grab it with your hand and hold on. What if you release your tension?

Thanks to that, two people were impaled on swords and flew through the air, drawing a large semicircle and falling down on the guy who was extending his sword behind him.

On the way, the sword came back, rustling.

A giant longsword imbued with starlight cuts through skin and bone, and with its remaining strength, it digs deeply into the solid ground of the mountainside.

"You bitch! Ximen-cheong!"

"Who are you, bitch!? Do you know me!?"

He swung his Moonlight Sword and kicked away the rushing Kang-Hwan, shouting, "Baek."

He will become the one and only swordsman who flies like a dragon, the Jeolnaksungjon Jun Gi-chung.

The new form of Qing was immediately split into eight.

The Jun-gi-chung, who had flown in with a cool sword, cut through the air and landed squarely on the innocent Sapa warrior.

"Euryaaaa!"

Among the eight translucent blues, the strongest blue cried out.

Qing, who had been sliding around in a standing position, regained his original color and slashed at another warrior!