\chapter{Journey to Taiyuan (1)}

The interior of the carriage was nothing short of luxurious.

The wooden finish was impeccably smooth, without even the slightest splinter, and the well-fitted wood was neat, without so much as a coin's gap between them.

There was even a brazier set into one wall, an extravagant feature that ignored the basic principle of carriages, where one had to endure the heat in summer and the cold in winter.

On one wall, a spacious seat, more than a chair but less than a bed, was prepared for honored guests, and in the middle, where translucent silk hung.

There was one figure, languid and bored, with their hand shoved into the chest of the woman beside her, continuously fondling.

"Are you perhaps curious about how much more squeezing is needed before it bursts? Cease your harassment of your sworn sister, Tianhuajian. I fear others may see."

"Huh? I'm fine with it, though?"

"You are also a problem. Are you not ashamed in front of others? Why do you naturally offer your breasts? It is an inappropriate attitude to display in front of others, no matter the circumstances."

"But I'm her Yi-mei, you know? Shouldn't it be okay to let her touch my chest?"

"This Rang Rang cannot understand. Is it normal for a younger sister to harass her older sister's chest?"

"Honestly, I don't know! I didn't have any sisters before Xiao-mei. But shouldn't I let Xiao-mei do whatever she wants?"

"You're absolutely unreasonable. You are a surprisingly formidable opponent in your own way, too."

"Yup. Of course! I'm a Master now, too."

"No, that's not it. Honestly……"

Rang Rang swept her face with both palms.

Regardless, Qing just absentmindedly poked and stroked the soft flesh that fit so snugly in her hand, spreading her fingers wide to grasp and release, enjoying the fullness that filled the spaces between her fingers.

"It's just, Xiao-mei just likes breasts."

"Even if you try to pass it off as normal, it is a very peculiar scene. Ordinary sisters do not grope each other's breasts. Especially not in front of others."

"It's just. Xiao-mei's mind is a bit complicated."

Gyeon Pohui threw out a gentle smile.

Rang Rang paused, stopped what she was about to say, and eventually just shook her head.

"This is utterly humiliating. To think that this Rang Rang's insight is inferior to such a pure-hearted human. Pretending to be foolish while making a fool out of others. This Rang Rang will acknowledge that I have underestimated you. The Tianhuajian's act of harassment is a manifestation of an unstable emotional state. Tianhuajian, do you agree?"

At this, Qing, as if suddenly regaining focus, looked at Rang Rang.

"Huh? What?"

"Your breasts."

"Right. Breasts. Why breasts? There are other soft and squishy parts, right? Like the inner forearms or the belly."

"This Rang Rang cannot grasp the context of this conversation. However, it is interesting, so please continue."

"Listen. Breasts vary in size, shape, and texture from person to person. Yi-mei has really big ones, and they're so soft that they feel like they're flowing through my fingers, you know?"

"This was information I did not particularly wish to know."

"But then there are people with small breasts, right? To the extent that their forearms or belly are softer in comparison? But strangely, it's not as satisfying as breasts."

"Hmm. Very interesting. So?"

"So, breasts, as breasts, have an allure that draws people in. Therefore, I don't need any more reason than that to touch Huimae's breasts."

"A grand justification. So this act of harassment has nothing to do with the Cheonhwa Sword's emotional instability."

"Yeah. I'm fine. I'm not bothered at all. I'm very normal. Just like usual."

"Let's just say that's the case for now."

Qing's dispatch period was until winter.

Although an unexpected extra month was added due to the intercalary month.

Now, it was March.

It was the beginning of spring, called the third month of spring.

Since Qing fell into this primitive, ancient China sometime around spring, it could be said that her sixth year of Wulin life had now truly begun.

Qing was a quasi-Unrestrained Realm level Supreme Master who had already beaten several Unrestrained Realm Masters.

However, that did not mean she was in a position to actively intervene in the complex affairs intertwined with the Wulin Alliance, the Unorthodox Faction Alliance, and the Blood Cult.

"I cannot thank the Cheonhwa Sword enough. The Cheonhwa Sword is truly the benefactor of the Jin Clan."

"Th-That's, it almost sounds like you're saying goodbye."

"Well. Isn't it time for the Cheonhwa Sword to return? Winter has passed, so the Cheonhwa Sword must return to her sect, no?"

"But, the Blood Cult bastards are still around……"

"Originally, the Blood Cult bastards are those who immediately cut their tails and hide as soon as even the slightest thing goes wrong. Since their conspiracy has already failed, from now on, it will be up to the Alliance to conduct a large-scale investigation."

"But, the disciples haven't even arrived at the Jin Clan yet, so……"

At this, Jin Jagang smiled contentedly.

"Strictly speaking, preventing the Blood Cult's conspiracy was also thanks to the Cheonhwa Sword's efforts. I understand why the Godmother praised you so much. How could she stay quiet with such a well-raised disciple? In fact, I should say she's been exercising restraint."

"Hehe. It was nothing."

"I, as an elder of the Orthodox Faction, am also ashamed to face the Cheonhwa Sword. So, leave the future matters to the adults."

Honestly, there was nothing more for her to do in Guangzhou even if she stayed.

The Guangzhou Unorthodox Factions were utterly crushed, their pillars practically pulled out.

It was firmly imprinted in people's minds that they shouldn't mess with the Unorthodox Factions, so there shouldn't be any major problems for the Jin Clan in taking in disciples.

So, if she were to stay longer, the only thing to see would be, well…

Lady Jin's shocking low-cut hanfu?

…was what she thought.

"I made a few sets of clothes for the Cheonhwa Sword."

"Wow. Thank you! You really didn't have to."

"No matter how much one says that clothes are completed by the face… You have such beauty, yet your sense of fashion is terrible. Especially for women with large breasts, clothes don't always fit well."

"I don't think it's that bad……"

"No. Among the people I know, the Cheonhwa Sword is the worst dresser. Honestly, it's terrible, almost a crime."

Jin Seol firmly stated.

And so, Qing tried on the clothes.

"Hmm, Lady Jin? Isn't this a bit… I mean, this is just… It feels like there's no difference from being naked."

Qing cringed in embarrassment as she wore a thin skirt that was cinched up to her rib cage, just below her breasts, with a sleeveless vest over it.

The vest, with silk only in the front and the top and back exposed to the wind, was so short that it barely reached her solar plexus.

With her already heavy breasts, the round curve below was fully exposed to the world.

What is this? Isn't this just being topless? It's just indecent exposure, isn't it?

If I look up from below, I'll be able to see the nipples.

No, wait, how can I even jump around wearing this?

It's so flimsy that it'll just flip up, and then I'll just be a pervert running around with my breasts exposed.

However, Jin Seol was serious.

"It's said that this summer will be especially hot, and at the end of last year, there was a trend of very bold expressions, wasn't there? It seems that Young Master Jade Qilin is very interested in low-cut hanfus. So, the fashion trends for the upcoming summer will likely be even bolder, openly revealing beautiful curves, right? Especially for women with large breasts like the Cheonhwa Sword, look, your waist is completely exposed, isn't it?"

And so, she tried on the several sets of clothes that had been made.

"Um, Lady Jin? Isn't this too revealing? It's too, um, you know, a bit too much skin is showing."

"Young Lady Ximen, have you been living in the Spring and Autumn Period or something? I mean, even Young Master Peng would just say it looks good. It's just showing a bit of the upper chest."

"Uh, Lady Jin? This, why is there no fabric covering the solar plexus? There are only two lines in the middle? Did I wear it wrong? What's going on? Did I put it on backwards?"

"Young Lady Ximen has such large breasts, yet your upper chest is so defined. It's a requirement for beautiful breasts, after all. It looks good."

Each and every one of them made one look like a person with severe exhibitionism or someone overly obsessed with showing off their body.

"Uh, Lady Jin? I don't think a low-cut hanfu suits me……"

"The top doesn't matter. If it's really too difficult, you can find another jacket. The completion of clothing is in the skirt, after all. Anyway, try to wear them out as much as possible. It's such a waste to have such a pretty figure."

In Zhongyuan, women's attire was divided into skirts and everything else.

Unlike Qing's hometown where tops and bottoms were separated, here they wore a skirt and filled in the rest.

Thus, skirts in Zhongyuan could be worn over the shoulders, wrapped above the chest as a single piece, worn below the chest, over the abdomen, or even on the pelvis, existing in all lengths.

And there were straight-falling skirts, skirts with many pleats that fluttered, skirts that were wide and loose, skirts folded largely and neatly, skirts that emphasized the buttocks by cinching below them, and so on. Their shapes also varied greatly.

It was the most important element of clothing, starting with the skirt and matching the rest to complement it.

Therefore, the clothes Jin Seol had made always had the low-cut hanfu as an additional element. In the end, the true value was in the various types of skirts.

In fact, Jin Seol's handmade skirts were a luxury that every woman in the Orthodox Wulin dreamed of.

They say that small differences make luxury.

When Jin Seol made them, even with subtle differences, they somehow enhanced one's figure and made them look beautiful.

"Hmm. I'll wear them well. Though the low-cut hanfu is a bit much."

"I wish I could have made more, but I was so busy with work."

At this, Qing looked down at the large bundle of clothes she had to hold with both hands.

Qing had never made clothes before.

However, she could tell that making this many clothes would have required practically all of her time outside of work to be spent on needlework.

No, even that might not have been enough.

Is she some kind of human sewing machine?

Thinking about Jin Seol, who had been sewing all this time, she felt a warmth spread across her face.

"Thank you. I'll wear them well."

"I'm the one who should be thankful. In many ways."

And then, Qing read the atmosphere.

Ah, this is the moment where I should give a hug.

At that, Qing triumphantly spread her arms.

Jin Seol burst into laughter at the sight, then stepped into her embrace and hugged her tightly.

And on the day of their departure, Yeom Huiyoung sat on the driver's seat of a carriage pulled by six horses, triumphantly pointing behind him with his thumb.

Wait, where did he even get something like this?

Even stables don't rent these out, you know?

But well, what's good is good, right?

Thus began their journey home.

However, Zhongyuan was vast.

Heading north from Guangzhou, they passed through Qingyuan, Yangshan, Lianzhou, and at the southernmost tip of Hunan Province, Yizhang, then Chenzhou, Hengyang……

Even when they had just left Guangzhou, Qing was still excited, looking out the window and radiating murderous intent, thinking she would destroy any Blood Cult bastards she came across.

But who would have known that Blood Cult bastards wrote ‘Blood Cult' on their faces? How could she possibly know who they were just by looking?

Moreover, the current communication technology of the Blood Cult had transcended the times.

Who could have imagined that there were Jiangshi capable of conversing with other Jiangshi far away?

In fact, even the person who made them didn't understand what these beings were, how they could have such abilities, how they could converse with family far away, and found it all very strange.

Anyway, although Qing was filled with murderous intent, thinking she would kill all those Blood Cult bastards, that only lasted for a day or two.

Traveling by carriage was a way to abuse one's ass in exchange for the convenience of not using one's legs.

However, since the carriage was so luxurious, their asses were also comfortable. As such, when the body was comfortable, the treacherous human mind naturally wandered.

So, random thoughts crossed Qing's mind.

What was a good person, what was a bad person, and what was the difference between a utilitarian good person and one who was good to an individual?

And what was wrong with killing bad guys, and, well, why is it that no matter how much I fondle Sworn Sister's breasts, I never get tired of it? Could there be drugs applied to them? Then, is it the only drug allowed by the nation? It's not. Looking at the artifacts of primitives, sculptures with huge breasts didn't just appear out of nowhere, I'm sure……

And the carriage continued to roll.

Towards home sweet home.