\chapter{Journey to Taiyuan (7)}

Taiyuan, the capital of Shanxi Province!

Taiyuan may or may not be a very meaningful land to Qing.

Because, the spiritual root of the Ximen Qing, the hometown of the Korean people, the city where ancestor Dangun (also known as Tan'gun Wanggŏm) established his kingdom, is Taiyuan!

There are retarded people who claim that.

According to the opinions of these idiots, the shocking fact is that the first hometown of the Korean people, Shinsi\footnote{ (신시; 神市; 'City of God'}, was this Taiyuan land, and that the former capital of Goguryeo, Jolbon, was this Taiyuan.

The square, neatly built castle surrounding Taiyuan is a testament to the magnificent technological prowess of the Goguryeo people.

Just one listen will reveal how convincing these idiots' claims are, backed by scientific evidence and historical data.

It is said that Dangun established Shinsi between Baeksan\footnote{Changbai mountain} and Heuksu\footnote{Hei river}.

Surprisingly, the land of Shanxi Province, where Taiyuan is located, has mountains and rivers!

What's even more surprising is that the name of the river is Hei river!

What's even more surprising is that the mountain's name is not Changbai!

But why is Shinshi called Taiyuan?

Originally, there was also a Changbai Mountain, but it is claimed that the Chinese people hid and erased the name Changbai Mountain in order to conceal the dazzling history of the great Hwanguk\footnote{ancient empire depicted in pseudohistorical book 'Hwandan-Gogi} people.

There is no evidence, but it used to be Changbai!

In fact, just a fortnight south lies the warmest and most bountiful land for humanity in a time when the world was much colder and harsher than it is today.

However, it does not explain why they had to crawl further north, where it was colder, and why they had to crawl towards a land surrounded by mountains on all sides, including the north.

Perhaps it is because it is not superficially drawn, so we can guess that it is unknown.

In any case, without even realizing it, Qing had reached the birthplace (or perhaps the place) of his spiritual people.

Maybe that's why her heart didn't pound with any meaningful excitement.

In any case, it may be because the Qing body has nothing to do with the Korean people.

Anyway.

Hanlin Academy was located in Taiyuan.

Of course, there was no such history in the Qing's homeland.\footnote{the original Hanlin Academy was located in Chang'an}

Originally, it should have been in its prime and had a place in the palace.

But such differences are not something Qing can know in detail, and in a world where people fly by holding onto the energy of nature, what difference does it make whether Hanlin Academy are in Taiyuan or Hangzhou?

It is a well-known fact that as the current imperial family gradually distanced itself from Confucianism, the Confucian scholars who were displeased with this settled down in places that were close but distant.

Taiyuan is close to Beijing, but in reality, it is far because you have to go around it via Henan in the south.

Although they are far away from the capital, this location is chosen with the hope that they will be used again and receive attention from up close.

And the headquarters of such Confucian scholars, is the Hanlin Academy.

The guard guarding the entrance to the Academy sees a somewhat strange visitor.

A tall woman wearing a cotton veil, and a small child holding her hand tightly.

The child looked around curiously, then looked up at the big woman and opened his small mouth.

Of course, if you look at it this way, they look like an ordinary mother and daughter on a trip.

What was odd was that both women were carrying swords.

The sword carried by the little child is large compared to the child's size, reaching up to her ankles, and the sword carried by the large woman is also large, reaching up to her ankles.

\textit{What is it? A mother and daughter from the martial arts world?}

Isn't this a peculiar word that doesn't come to mind even when you think about it?

Come to think of it, of course every woman in the martial arts world has a mother, and I wonder what's so special about a mother and daughter walking hand in hand.

Yet, somehow, it is an extremely rare sight.

Still, it seems that you need a certain philosopphical disposition to work at the Hanlin Academy, so why does the image of the mother and daughter look strange just because they are martial artists? Why is it considered unusual just because they are carrying swords in a scene of a mother and daughter out for a walk? And why has the sun not even risen an inch yet when it seems like it has been ten o'clock since they started work?

In fact, it was a shallow thought that was just a waste of time rather than a reflection, so while I was becoming a wise man who had forgotten where I was and who I was,

"Excuse me?"

When he came to his senses, the mother and daughter were right in front of him.

The guard suddenly came to his senses and lowered his voice to a solemn tone.

"Huh, ahem. This is the Great Study Hall of the Hanlin Academy. It's also a great cradle where the world's scholars gather to grind jade and make needles. What is your business, Madam?"

"Madam? Well, anyway. I came to see the Scholar of Teaching. Is he inside by any chance?"

"The Scholar is currently attending morning lectures. What's going on?"

"Oh, my name is Ximen Qing, a disciple of Master Tian Yuxue. I have come to visit him."

The guard stares intently at Qing's veil, and eventually concludes that no matter how much he looks, he cannot see inside.

As Qing tilted his head wondering why this old man was acting like this, the guard opened his mouth with difficulty.

"Madam? I never heard the Scholar of Teaching say he teaches women. There must be some misunderstanding…"

This is why Ximen Surin disparages the Hanlin Academy by calling them Confucian bastards.

"Oh. Right. Just a moment."

The woman deftly turns the luggage forward, rummages inside, and pulls out a bundle of freshly folded, crumpled, and crushed letters.

And then she spread it out and handed it to the guard.

When the guard received and unfolded the scroll, it reads ‘Ximen Qing, the beloved disciple of the Scholar of Teaching Tian Yuxue, receives the call of the master', with the four characters of Scholar of Teaching stamped in red.

Only then does the guard bow his head deeply.

"Excuse me. I'll take you inside."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

It is said that even if the Emperor comes to visit while the lecture is in progress, you must wait.

It was a story that the guard told her without her even asking if she could go see the teacher.

It was also a statement full of pride from the Hanlin Academy, which was once the teacher of the Crown Princes and also the teacher of the Emperors.

So, as Qing was enjoying a cup of tea and looking at the well-decorated artificial waterways, a loud chatter suddenly broke out.

"Ah. I guess it's over."

As expected, people are pouring out of the largest building in the center of the wide-open artificial waterways.

They all had a face filled with a sense of freedom, almost like liberation, and a bright smile that was characteristic of those who had endured something.

It was a mystery how so many people could remain so quiet and keep their mouths shut.

Qing stand in front of the stairs and check the passing faces, wondering if the teacher might pass by.

The morning lecture was finally over, and the students who had been whispering about what to eat for lunch and such looked at Qing with a puzzled expression.

'Why is there a woman in the middle of the Hanlin Academy?'

'It's not the Jinan area, but she's standing guard in front of Great Study Hall?'

'But she's really tall.'

'Who's next to her? Is it her daughter?'

But a gentleman does not become obsessed over a woman.

Although it was curious and exciting, no man bothered to ask questions, so they just split off to the left and right and passed by behind.

Then, Qing finally shouted loudly.

"Master!"

Tian Yuxue was making eye contact with several men and was coming down the stairs in elegant stride.

Tian Yuxue's head snaps up at the sound of Qing's voice, and a bright smile appears on his face.

"Oh my, disciple. You're here now? If you're here, why don't you come into the hall, give greetings, and listen to the lecture? Why are you waiting at the bottom of the stairs under the bright sun?"

"Hehe. They say that even the Emperor shouldn't intrude during a lecture."

"Of course, that's what it means if he came as the Son of Heaven. A lecture is something that anyone can attend if they wish to learn."

"Hehe. Actually, the lecture was a bit… Ah, this is my younger sister, Chen Changming. Changming, please say hello. This is my teacher, Elder Tian Yuxue."

"Hello."

"Yes. How are you, young lady? I thought you weren't coming since it was past your time to come. Nothing happened since you came, did you? Have you eaten?"

"Hehe, I was planning to eat with you, Master. Do you know the best restaurant in Taiyuan? I'll treat you properly today."

"After coming a long way, the teacher should first feed his disciple. How can you treat me if you have to ask for direction? So, let's go home for now."

The scholars of the Academy exchange glances with each other.

'A huge news!'

'The teacher had a woman as his disciple!'

'She's a beloved disciple, a disciple whom the dignified Scholar of Teaching is so happy to see that he can even smile brightly.'

'Hmm? But what's with the swords?'

'The teacher took a martial artist as his disciple?'

'It's not uncommon for women to carry a sword for deterrent, as it's dangerous for them to travel alone, but isn't that a truly impressive sword?'

But the people who had the correct answer to that question were already giggling and leaving.

At lunch today, everyone will let their imaginations run wild.

Anyway.

Tian Yuxue's house was a huge mansion, a large courtyard that seemed to have been pulled in at a sharp corner, even among the courtyards.

Qing asked with a sour expression.

"Huh. Master, you're living really well, aren't you?"

"Haiyaa. How can you study when you're hungry and on the verge of starvation? If you don't have to worry about making a living, you can read the scriptures in peace. I might be the greatest teacher in the world, but I can just babbling about because my family is wealthy. Since my family has so much money, all I had to do as a child was study."

Chen Changming's eyes widened and he looked up at Tian Yuxue.

Because Tian Yuxue was a person who became rough with his speech as soon as he got home.

"Something like Nangying Yingxue? Is that right? Didn't they say something like that?"

囊萤映雪. Firefly in bag, reflecting on the snow.

Che Yin of the Eastern Jin Dynasty collected fireflies in the white silk bag and used them to read, and even held the high position of Minister of State.

At the same time, a man named Sun Kang succeeded in rising to the high position of Censor by reading under the moonlight reflected by the snow.

One might say, why don't you just turn on the lights?

Since they didn't have money to buy oil, they read books in the middle of the night in this way that didn't cost any money.

In other words, it is a saying that praises the effort put into studying despite great difficulties such as poverty.

At that, Tian Yuxue snorted.

"Che Yin and Sun Kang, what did they do after studying so hard and becoming officials? They ended up becoming corrupt officials who diligently exploited the people. They didn't become great men, they just became big dogs. It wasn't that they had any interest in studying per se, but rather that they chose to study to enter government service and exploit others."

Tian Yuxue clicked his tongue and continued speaking.

"For them, studying wasn't about becoming great, but rather a means to amass wealth and avenge poverty. Therefore, only the wealthy should study. Otherwise, the purpose of studying would become the pursuit of wealth and honor, not personal perfection."

"Ohhh."

Tian Yuxue adds to Qing's exclamation with a sound that is unclear whether it is laughter or mockery.

"Why, does that sound like something a Confucian scholar shouldn't say?"

"No. I don't know about that, but since you said so, I think you are a truly learned person."

"This brat."

"But my teacher is not the stern Scholar of Teaching, but the elder Tian Yuxue, so it shouldn't matter, right?"

\textit{I didn't come here to learn from the scholar, I came here to learn from the Divine Thief.}

At Qing's words, Tian Yuxue's expression became mean.

"Do you really think so?"

"Sure?"

"Dashi told me that your head was no different from a roadside pebble stone. You already had memorized the basic scriptures of Daoism, so she earnestly requested that I teach you some Confucianism throughout the year. But, disciple, Confucianism is quite extensive. Have you heard of the Hundred Schools of Thought?"

"Huh."

"Did you think you came to play? Disciple, you came to study. I am considered one of the three greatest teachers in the world. How can you, a disciple, be so ignorant?"

"Uh, I haven't heard anything like that……"

Qing's expression distorted.

\textit{Studying writings?}

\textit{Studying writings!?}

"Don't be too annoyed. If you keep doing it, you'll find it surprisingly fun."

"That kind of fun doesn't exist."

"No, really? Look at me."

"That's why you became such a great teacher. If everyone could experience that fun, then all rich young masters would have become great teachers. They'd study for fun and attained enlightenment."

"Oh, really. Looking at it this way, I don't think you're stupid. Are you the kind of person who's smart but doesn't use your brain? Well, it's an order from Dashi, so what can you do no matter how much you try to avoid it? Come on, I see that girl were also sent here alongside you because she's bored with her studies."

Chen Changming blinked his eyes. And blinked again.

Then, she let go of the hand she was holding tightly and looked into the distance.