\chapter{Journey to Taiyuan (5)}

The higher the realm a martial artist reaches, the more they must increase the weight of their ass.

This means that a heavy ass should not move around frequently.

Trivial tasks are for Second-Rate martial artists.

Errands should be given to First-Rate martial artists.

Those of the Peak Realm should wait until at least one out of ten subordinates have died before making a solemn appearance.

As for Transcendent Realm martial artists, they only show up after everything has gone to hell, making a belated entrance.

But when it comes to the Unrestrained Realm?

If an expert of such a caliber moves carelessly, disasters follow.

Why? Because if an expert of the Unrestrained Realm moves, another expert of the same realm must move as well.

Then, as grudges in Wulin go, they will be dragged out one by one, all rushing out into the open.

The ways of Wulin are similar to those of children.

Though they may act dignified and pretend to be mature, it ultimately comes down to hitting and fighting.

However, the problem is that fights between those of the Unrestrained Realm do not end with bruised eyes and mothers showing up to make their kids apologize while standing with their hands raised, like seven-year-old snot-nosed kids.

When those of the Unrestrained Realm fight, it's practically a scene of natural destruction, a wasteland as if bombs had rained down.

If it were in a deserted field, the field's owner would be the only one shedding tears of blood over their ruined crops.

But what if they fought in the middle of a city?

In Qing's homeland, this phenomenon was known as mutually assured destruction. If the Unrestrained Realm had a gathering, the post-gathering party would be held in the afterlife.

It's a grand farewell to the living world that hundreds of thousands, or even millions if exaggerated, would attend.

Therefore, even someone like Bu Anpyeong, the current Lord of the Four Great Evils, had to act decently, despite his naturally light demeanor that defied gravity and made him float around.

His ass should be heavy and glued to his seat.

However, the weight of his actions was extraordinary precisely because of this.

But Bu Anpyeong had personally made a visit to protest the bloodshed in Guangzhou.

It was a declaration that the Four Great Evils would not stand idly by regarding this matter.

For Bu Anpyeong himself, he was determined to somehow find a pretext to take over Guangzhou.

If it was the Jin Clan, he couldn't just erase them, but he could at least force them into seclusion for about five years or chase them out to another region.

Thus, Bu Anpyeong thought to himself.

Dammit. I shouldn't have come.

Even experts of the Unrestrained Realm couldn't make life go their way.

"No, the Blood Cult? What the, fuck."

"Didn't I tell you to wait for the investigation results first?"

"Who would have thought the Blood Cult was involved? I thought those Guangzhou bastards were just making things up, collaborating with some medicine peddler."

In fact, when they arrived, there was no need for an investigation as rumors were already rampant. As such, there was no need to confirm its authenticity.

The strategists did do some work since they had already come.

The Wailing Moon Sect had created cursed monsters of the Blood Cult, using evil elixirs provided by the Four Great Evils as materials.

The Guangzhou Buddhist Temple and Geumjeok Gang were destroyed before that, but they had also spread rumors that they received elixirs from the Four Great Evils.

Luckily, they were destroyed before that. If not, there might have been three Blood Ghouls running rampant.

"E-Excuse me, Lord?"

The leader of the Balhyuk Sect's voice trembled.

It was only natural for his voice to tremble, as he had brought the Lord of the Four Great Evils to his sect, which was a Third-Rate sect at best.

It would be even more so if it was not for a good reason.

"What? What is it?"

"Uh, th-that, Jin Clan Lord… He sent word again, asking when you will be available to meet……"

Bu Anpyeong's expression soured.

This wasn't the original plan.

He was supposed to have lined up experts of the Four Great Evils like folding screens, then made the Jin Clan Lord kneel as he interrogated them on their sins regarding the massacre.

Instead, it was the Orthodox Faction who were excited, urging him to come and see them, asking if he had something to say.

"Tell them the Lord of the Four Great Evils has gone home."

"Pardon?"

"Tell them I went home."

Bu Anpyeong spat on the ground.

"Strategist, pack up. We're going home."

In the end, what else could he do?

He left in high spirits, only to end up stuck in a small, insignificant unorthodox sect in Guangzhou without accomplishing anything before returning dejectedly.

His dignity was utterly lost.

But what could he do about it?

If the Lord of the Four Great Evils took action himself, it would become the official stance of the entire alliance.

If he apologized, it would be like admitting the fault of the Four Great Evils.

Admitting fault in matters between organizations meant giving up corresponding rights and interests.

So, he couldn't do that.

If he tried to act tough and claimed they would not stand for the slander against their members, the whole world would gossip about how the Four Great Evils had joined hands with the Blood Cult.

So, all he could do was quietly return and announce their official stance.

‘Our Four Great Evils Allied Union is not related to the bloodshed in Guangzhou in any way.'

‘It's just a vile scheme by the Blood Cult to use the name of our Four Great Evils to incite division among the Orthodox Wulin.'

‘You're not the only victims. We're victims too.'

‘But we will step back from Guangzhou, so let's just let it go at this point, alright?'

"Those Blood Cult bastards. They were actually being helpful for once, selectively targeting and destroying only the Orthodox Faction. But still, they are absolutely useless. I should just tear them all apart and kill them, those fucking bastards."

"Think of it positively. At least thanks to you, Lord, the Orthodox Faction doesn't suspect our Four Great Evils, right? It's all thanks to your leadership."

"Fuck."

After all, the Lord of the Four Great Evils had personally come to protest the bloodshed in Guangzhou, only to turn around without even showing his face.

It meant that he came without knowing about the involvement of the Blood Cult.

It was a severe blow to the dignity of the Lord of the Four Great Evils, but it proved his innocence in a roundabout way.

And that was why Bu Anpyeong's stomach was churning.

Proving his innocence, my ass.

The Blood Cult was involved, so those excited were the Orthodox Faction. In reality, the actual victims were the Four Great Evils.

There was also one particularly annoying person.

"Hah. Strategist, should we just leave that Heavenly Flower Sword brat alone?"

"Now there's a bit of a lack of justification. If you hadn't gone to Guangzhou, it would have been one thing, but…"

"Why! What about that bitch? How laughable will she think the Four Great Evils are? She was acting all righteous in Nanye, wasn't she? Some Righteous Knight, my ass. If it wasn't for the Blood Cult, she'd be nothing but a killing star. A slaughtering star."

"Since the Blood Cult was involved, it doesn't matter. What are you going to say? ‘We were deceived by the Blood Cult and tried to make a monster, so we are innocent and good people of the Four Great Evils, but she still attacked us, so we can't forgive her'?"

"What about the Nanye incident?"

"What will you say about that as well? Are you going to say we tried to destroy the Gyelim Sword Sect, so she massacred our innocent combat unit? And the Nanye incident involved the royal household, not the Heavenly Flower Sword."

"I know! I know, okay?! Can't you just sit there and go ‘Yes, yes, that's right'?! Why so snarky?! She's just a brat at a high realm, and every little thing she does is so irritating!"

It was common for young talents to cause trouble due to their youthful vigor, performing feats like slaying evil.

However, the damage from such actions was usually not significant.

This was because young talents were fundamentally weak.

Of course, some of them were at the level of Peak Realm martial artists, but those from prestigious families were taught from a young age that they represented their sect and family.

So even though the youths from prestigious families could be considered high-level martial artists, they didn't just draw their swords and go around shouting, ‘Slay the evil!', acting recklessly.

This meant that those who went around wielding their swords, shouting for the death of bad guys, were usually just inexperienced brats.

And dangerous brats tended to avoid mindlessly wielding their swords.

But what about now?

The Heavenly Flower Sword was at the Transcendent Realm.

She was a Master who could wield Sword Force.

What if such a person went around saying all evildoers must die, recklessly swinging her sword?

The Guangzhou Buddhist Temple was a prime example.

She was enraged by the fact that a few commoners were slain and stormed in to massacre them, they said.

Honestly, which unorthodox faction didn't kill a few commoners here and there?

It was common practice to kill a few commoners as a display of power to make them more obedient.

So if they let the Heavenly Flower Sword be, how far would she go, killing as she pleased?

Would they have to tolerate a bitch going around burning down unorthodox factions?

And all the while, she would gain popularity among the people through her so-called righteous acts of slaughter?

It was a time for the alliance to take action.

But it just so happened that the Blood Cult had intervened and messed everything up.

"Just endure it for a little while. Do you think a wench who was so impulsive and reckless will suddenly become calm and composed? She might have been lucky so far, but won't she eventually cause a huge mess?"

"I'm frustrated! That's why I'm frustrated! We have to declare her an enemy of the Four Great Evils before the Wulin Tournament! If we declare it after the tournament, it will look pathetic!"

"Hmm."

The strategist, Sun Woong, also had no particular solution to this.

However, as they say, the answer was often unexpectedly close.

"Lord, that Heavenly Flower Sword… She… She……!"

At the afternoon reception, a young man named Wang Dae-yang, the third son of the Green Forest's Chaeju Wang Cheol-gun, suddenly fell to his knees and started wailing.

At this, the Lord of the Four Great Evils and the strategist exchanged glances.

‘She's already caused trouble, hasn't she?'

‘It seems like she's already caused trouble, hasn't it?'

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Seomoon Soo-ryun was troubled.

The subjugation of the Green Forest was no ordinary feat.

Of course, it wasn't common for one to single-handedly attack the main camp, behead the leader, and set the stronghold on fire.

It was indeed an event that would shock the whole world, regardless of whether it was actually possible or due to some trickery.

But what Seomoon Soo-ryun considered extraordinary was not about who the opponent was or whether it was possible.

If we put it simply, it was just about dealing with bandits.

If it was just burning down a shabby cottage in a local mountain, she would have just praised Qing, saying it was a common act of a chivalrous person.

However, what if the shabby cottage was changed to the main stronghold and the local mountain to Mount Cheonja?

Could she still scold her disciple for being too rash, even though she had just dealt with such an enormous entity?

Was there a law that said one could kill small-time thieves but not big-time thieves?

"Hmm."

Seomoon Soo-ryun pushed aside the paper on which she had been drawing orchids.

It wasn't just a matter of chivalry, but also a matter of grudges.

If the leader was beheaded and the main stronghold burned, then if someone were to gather the bandits to rebuild the Green Forest, or after it was rebuilt, they would have to start by avenging her disciple.

If that was not possible, they would have to wait until Qing grew old and died.

Conversely, it meant that defeating Qing would make it easy for anyone to absorb the Green Forest.

Moreover, the Green Forest was a force that anyone could easily covet.

Additionally, the actions taken while staying in Yanggwang were also problematic.

Destroying an unorthodox sect's combat unit?

To openly storm into someone else's sect and wield a weapon?

However, she did not want to scold her disciple by saying that she was too rash, considering the circumstances.

What was she supposed to say?

That it's good to be chivalrous, but pick your fights?

Even though they are evil, consider the face of the unorthodox sects?

Because if you don't, you'll be in danger?

Prioritize your own safety before acting chivalrous?

She had never lived her life bowing down to such cowardly logic.

Why is a mad dog called a mad dog?

Because it bites everyone indiscriminately, that's why it's called a mad dog.

Therefore, Seomoon Soo-ryun's worries deepened.

If she sent her out into the martial world, her disciple's upright and firm sense of justice (justice!) would surely cause more trouble.

With just her martial prowess as a Transcendent Realm expert, how could she handle those grudges in the harsh and perilous martial world?

This made her regret her disciple's realm for the first time.

She had been satisfied with her being the youngest Transcendent Realm expert, but now that she thought about it, she realized the greed of humans was boundless.

However, the Unrestrained Realm was not something one could reach in a day or two, unlike the Transcendent Realm.

And she didn't want to stop her disciple's journey in the martial world, which had just begun to contemplate the meaning of chivalry.

Then what should be done?

For now, it would be best to divert her to a safe place.

And as it happened, the next schedule was just that.

Moreover, if it was with the great scholar of Confucianism, it might be of great help to her disciple's struggles.