\chapter{Journey to Taiyuan (8)}

\textit{This little brat?}

\textit{Is she already trying to ditch me?}

"Changming'er?"

Qing, whose eyes were twitching, stretched out his hand.

Chen Changming looked at the thin, white fingers with solemn eyes-

"Oh. A butterfly."

Suddenly, she turns her head to find the butterfly.

\textit{This little brat? She really doesn't want to study, is that it?}

\textit{Chen Changming's shameful attempt to escape from her studies will be punished later.}

"Ah. That's right, Master. Here is a gift from the heart of your disciple."

"Huh. Why are you bringing all this stuff?"

Tian Yuxue snatches the box that Qing has offered and opens it, hoping to get something out of it.

Three new, never-used calligraphy pens: one thin, one thick, and one very thick.

Tian Yuxue, who ran a brush over his hand, burst into laughter.

"What is it, marten's hair? Isn't it quite expensive?"

"Maybe. I picked it up."

"Yes. You have to have picked up something like this to be worthy of being called my disciple. Who picked you up from?"

"Hey, that's not it."

These are the calligraphy brushes that the old man who was next to the Hag Yan gave her from the time she was in Guangzhou.

It was a kind of gift recycling.

No, it's not recycling.

It is a ‘redistribution' of gifts.

Anyway, Qing rarely has the opportunity to write, and when she does, she used whatever brush and paper in front of her, so she doesn't really have a need to use a high-quality calligraphy brush.

So, it would be better for the brushes to go to someone who can write better.

"Thank you. I'l use it well. But if you're going to bring a gift, why don't you get something really ornately decorated? There's that kind with a coral body and gold leaf."

"Huh? Is that your taste? Flashy?"

"It's not that. Wouldn't someone ask then, 'Where did you get that old-fashioned brush?'. Then I can brag about getting it from my disciple."

"Are you saying that you want to receive such a tacky calligraphy just to show off?"

"Huh. Isn't filial piety a big deal? Filial piety is about children giving something to brag about them."

Even though it's just a passing remark, it makes her feel incredibly dizzy.

Qing's expression is gloomy.

"Hmm. It's strange. You keep acting like you're a learned person, so I can't get used to it."

"Intellect doesn't come out of the blue. It should flow naturally. If you just babble about everything without any explanation or brag about how great you are, it just comes across as frivolous."

The faces that naturally come to mind.

\textit{Yeah, Zhuge Lixian is quite frivolous.}

\textit{And Simachunfeng? Fengchun? She's so bad, it's almost pitiful.}

\textit{Compared to that, look at Xue Ganom.}

\textit{He says he's not a smart person, but as soon as he opens his mouth, he exudes the scent of a learned person.}

\textit{Except when it comes to sexual harassment.}

\textit{Hmm. Now that I think about it, is the future of the Orthodox sects really okay?}

\textit{The two smartest guys are like that?}

Qing expressed great concern about the bleak future of the Orthodox sects.

\textit{Well, I guess they'll figure it out themselves.}

Qing shakes off her random thoughts and takes out other items from her luggage.

"Oh. Right. This too."

"Huh? What is it? A handkerchief? It's too fancy for a man's handkerchief. Wait, is this a treasure map?"

"Wow. You recognized it as soon as you saw it?"

"Let me see. I can't tell at a glance. Where did you get this? With treasure maps, the source is the most important thing."

"Why?"

"Well, if it's from someone with some serious weight, you'd think that's a real treasure map. Have you ever been to a night market? Whenever it opens, there's always a few guys selling treasure maps. Can you believe that?"

"Oh. Then how about that? It's something the Lulin's chief had."

"The Green Forest's leader? Hehe."

Then, Tian Yuxue burst into a bright smile.

"What, you're so happy? You're glowing ten times more than when I gave you the brushes earlier."

"Well, wouldn't that make you happy?"

"Do you like treasure so much?"

Tian Yuxue turns his lips once and speaks.

"Hey. Why wouldn't I be happy to receive a treasure map from my disciple? My disciple brought this treasure map from the leader of the Green Forest, so I'm proud of your accomplishment. Now you've become a real thief! Treasure maps are inherently bloodthirsty, so stealing and hiding them is the job of a Divine Thief. You've become a real Divine Thief too. I've chosen my disciple very well. Now I can retire in peace."

So, what he's saying is that the fact that a prospective Divine Thief stole the treasure map from the Green Forest's chieftain is both special and beautiful.

"So, let's hear a tale of bravery. How did you get it? How did you even know there was a treasure map? You even went all the way to Tianzi Mountain to steal it. Hehe."

\textit{It's not that I'm not happy, but I'm happy to have such disciple.}

\textit{I am proud and honored.}

\textit{How could I not be happy that a novice who had not yet finished her training had stolen a map that could be a source of trouble from the world's greatest bandit leader?}

\textit{Upon hearing rumors that there must be a treasure map, she realized hers mission as a Divine Thief and took risks to sneak into Tianzi Mountain to steal it.}

"Um. I just took it."

"…?"

Tian Yuxue's head stops spinning for a moment.

"You just took it?"

"Well, I was sightseeing in Zhangjiajie. Oh, you know Zhangjiajie? The scenery there is truly breathtaking. It's like something out of this world. The mountains are shaped like raised fists, and there are thousands of them—"

"You bitch, put your hands down. I'm afraid someone might see. What are you talking about, a dick?"

"Oh."

The Qing hid the mountain of fists that were shown with great impurity.

Still, she learned something.

In Zhongyuan, it seems they called that as 馬屌/ madiao\footnote{horse dick}!

And then she started a bloody battle with the Lulins.

It was a heroic tale of a passing female warrior who squarely and squarely defeated the bandits who were causing chaos in the world.

As the story ends, Chen Changming's eyes sparkle like starlight.

"Sister, you're amazing. You're amazing. You're a super hero."

"Right? I told you so."

"Haiyaa. So, disciple. You subjugated the Green Forest?"

"Hey, it's not like we're going to subdue them. Are there just a few bandits in the world? Well, the leader is dead and the other Unrestrained Realm masters have been taken care of, so they'll probably be more cautious from now on, right?"

"Haiyaa."

Tian Yuxue wiped his forehead.

Whether that was possible or not is a secondary question.

People who kill and take everything usually don't say they stole it.

\textit{What kind of Divine Thief is that?}

\textit{Divine Ro-, no, it's embarrassing to attach the Divine prefix, so she's just a robber and murderer.}

\textit{Come to think of it, she's not just a robber and murderer.}

\textit{A murderer of extreme intensity.}

"No, I told you to be a thief, so why did you become a robber?"

"Uh, um. What if you say you stole a life? If you're just stealing something harmful to get rid of, then stealing the lives of those useless bandits is ultimately the same thing, right?"

"Hmm."

At that, Tian Yuxue sighed deeply.

"Now I understand why Dashi asked me to teach you Confucianism."

"But, if we left those Green Forest guys alone, they would have just committed banditry anyway-"

"Stop right there."

Tian Yuxue cuts off Qing's words with a stern voice.

Because his displeasure was evident, Qing tried to shrink her neck and put her head between her shoulders.

Although Qing's body was superior to that of a human, it was not able to imitate turtle, so it stopped at the level of just making an effort.

Tian Yuxue clicked his tongue as he looked at the very intimidated Qing.

"I never once said anything wrong about you massacring the vicious bandits of the Green Forest. If I had to be specific, wouldn't you did the right thing?"

"Oh, really?"

Qing's expression brightens significantly.

Tian Yuxue continued speaking.

"I've read and reread countless scriptures from the sages, memorizing them, yet there are still many things I simply don't understand. Laozi said, 'If you look at the sky and see the sky, you'll see the sky'. Do you know what that means?"

"Hehe…"

Qing laughed. It meant she didn't know.

"The net of heaven may seem coarse, but it never misses even the smallest thing."

The net of heaven is the judgment on evil deeds.

What seems like a harsh judgment is that the judgment sometimes appears to be imperfect.

But since Lao Tzu\footnote{Another romanization of Laozi's name} insisted on adding this, he said that even if it looks like that, it doesn't miss even the smallest thing.

Evil deeds will eventually come back to haunt you, and wrongdoing will have consequences.

But is the world really like that?

Are the good blessed and the wicked punished?

No.

The net of heaven is so loose that the wicked easily escape.

Lao Tzu deceived, deceived, and deceived people with blatant lies that even a dog would not believe.

It must have been incredibly embarrassing for him to even bring it up.

"Hmm."

"So Sima Qian said, ‘Well, no, let's talk about this another time.'"

"Isn't that what Sima Qian said we should do next?"

"Yes. If you're as upright as you say, why is your voice so weak, and your face so ungainly that you can't even look me in the eye? 'I slaughtered those thieves. I cut them in half so they'd never rob again'. Shouldn't you be proud, your shoulders high and your nose high, as if you were boasting about your family's pride?"

"Hmm. That's…"

Qing pondered the answer.

But it just prickles her nerves like a thorn stuck in her throat and no answer comes.

\textit{Well, it was fun.}

\textit{If I have to kill someone to survive anyway, I'll kill those who deserve to die, so I can accumulate good deeds and satisfy my own happiness.}

\textit{A world where the world is good and the world is clean, this is the perfection of a world where no one gets hurt.}

\textit{Of course, bandits are not human, so they do not fall into that ‘who' category.}

It's not that 'Evil people should be killed'.

It's 'It is okay to kill evil people'.

That subtle difference, that small difference, is so huge.

"Lao Tzu, if that man wasn't naive and foolish, would he have spouted such unbelievable nonsense? Could he have truly believed that it's the way of the world that one's sins will ultimately come back to haunt oneself, and that one should live a good life and refrain from doing evil?"

"Sure?"

"Laozi himself didn't believe it. But he had to do it anyway. He knew it was a blatant lie, but in that era of atrocities overflowing in the Warring States, he had to spread the four principles of rewarding good and punishing evil. That's why he spoke such nonsense with such confidence. Even though he knew he was lying, he carried out his deception without a shred of shame."

Tian Yuxue pats Qing on the back.

"If you believe it is right and truly necessary, then you can proceed without any shame, even if it means deceiving and cheating all the people of the world."

It is truly a wonderful line coming from the mouth of a great scholar of the Hanlin Academy.

But what if it's the words of the Divine Thief?

You could say that a mere thief is talking big.

Isn't he just saying that you can steal other people's things without any shame in your heart?

"Hmm. I don't know. When you say something is right and necessary, who is it for? Me? Or the world?"

At that, Tian Yuxue smiles wickedly again.

"That's why you need to study. Once you've experienced the struggles of countless ancient sages from all walks of life, you'll be able to draw your own conclusions about your own concerns."

It goes around and around, studying the introduction, development, turn, and conclusion, and in the end it becomes a story about studying.

But after hearing this, you somehow feel like you really need to study.

This is the original method of famous instructors.

Before entering the class, the teacher grab the students' attention with a sound that touches their hearts.

But.

But where is this?

It is none other than the Great Study Hall of the Hanlin Academy.

It is the highest level educational institution in the current Zhongyuan, and it is comparable to a graduate school in the hometown of Qing, as it covers not only the basics but also the application.

Tian Yuxue is standing behind her with a solemn posture.

It seems like the class is conducted in a way that the Hanlin Academy students take turns presenting a given topic, and then ask questions or discuss it and exchange their interpretations.

"Here's a white horse. If a white horse is a horse, then isn't a black horse a horse? Isn't a yellow horse a horse? Then, can a white horse truly be a horse? Strictly speaking, a white horse isn't a horse. By adding the color white to a horse, a white horse becomes a unique group of horses, not horses. Therefore, although a white horse and a horse are the same, strictly speaking, they are not the same thing. Therefore…." (the White Horse dialogue, attributed to Gongsun Long)

"Shit, what nonsense are you talking about? If you have a really open mouth, do you think everything that comes out of your mouth is words? I think I'll just shove a carrot in your mouth."

The surrounding scholars are in an uproar, trying to hold back their laughter at Qing's sharp assessment.

What on earth does that even mean, to someone who lacks even the basics?

Unlike the scholars who have all come and gone at least once, Qing has no idea what they are talking about.

\textit{Whether it's a white or black horse, if it tastes good, isn't that the best horse?}
