\chapter{Journey to Taiyuan (4)}

Jin Jangmyeong wriggled.

But who was holding her but Qing, the human embodiment of monstrous
strength that even made Xiang Yu1 change his name to Namcheong?

No matter how much she squirmed, the firmly held embrace was as solid
as a mountain, without even a tremor.

"Eek, let go."

"Why? It's damp and sticky, hmm, not great. You said you'd let me hold
you if it was like this, so is this okay or not?"

"Let me down. Quickly."

"Sniff, sniff, let's see, does it smell like sweat? When did you last wash,
kid? I told you to wash behind your ears, didn't I?"

Jin Jangmyeong's struggles intensified.

Only then did Qing giggle and set Jin Jangmyeong down.

Jin Jangmyeong pouted.

"You're mean. I was training hard."

"Aha. You shouldn't just work hard. When I was your age, I had already
reached the Transcendent Realm."

"……? We're only a year apart."

"Yes. The youngest Transcendent, Ximen Qing. I didn't say anything
wrong, did I? How dare a mere First-Rate Realm try to talk back to the
Transcendent beyond Transcendent, the Transcendent of Transcendents,
the Super Transcendent Qing?"

Jin Jangmyeong's eyes narrowed into the shape of hatchet blades.

"You're so mean. I hate you."

"Alright, alright. It was a joke. I even bought a present for our
Jangmyeong. Let's see. Here it is."

Qing took out a box from the bundle, opened it, and was about to hand it
over when…

"Huh."

"What is it?"

"What the? Was it defective? Ah shit, I can't even go back to Guangzhou
to exchange it. This old man, I told him I was weak, but he insisted it
was sturdy."

It was a pair of small, scallop-shaped earrings, shimmering in five
colors, made from finely ground seashells.

Or rather, it was supposed to be a pair.

Upon opening, one of them was broken in half, the pieces separated.

Qing scratched the back of her head in embarrassment.

"Sorry. Did I bump it on the way? It shouldn't have, since it was filled
with cotton. It must have been defective from the start. I'll buy
Jangmyeong's present later-"

"No. It's okay. I can wear just one."

Cutting off Qing's apology, Jin Jangmyeong snatched the box as if afraid
it would be taken away.

Clutching the box tightly, Jin Jangmyeong followed Qing around,
chattering away as she unpacked.

"By the way, are we going to Taiyuan together this time? You're not
going to leave me behind again, saying you'll come later, are you? You
can't. I'll be angry."

"Hmm. Probably? They say the Wulin Alliance doesn't usually make
people work back-to-back like that."

"I don't like being left behind again. This time, I'm going with you
wherever you go."

"Jangmyeongie is too delicate, though. Hmm. For now, go wash up. I'm
going to see the Sect Leader."

When a disciple returned, it was customary to greet the Sect Leader
first.

Of course, in Qing's case, she wasn't exactly a member of the Divine
Maiden Sect, so it was a bit ambiguous. However, it wouldn't look right
to just skip Wang Juhee and run straight to Ximen Surin either.

Of course, Wang Juhee considered herself a mere figurehead, with her
name only listed in the Sect Leader registry.

Of course, it wasn't a self-deprecating thought in a negative way.

In fact, since she could just go to her Master for difficult decisions,
Wang Juhee's personal job satisfaction wasn't bad.

Anyway, a group had its order, and Wang Juhee greeted the lovely
youngest sister.

"You've come, Youngest Sister? Are you well?"

"What could happen? Have you been well, Sect Leader?"

"Me? How do I look?"

Originally, Wang Juhee was a master of self-concealment, to the extent
that she was called the Heavenly Concealing Sword due to her lack of
presence.

But that presence had grown significantly.

She had become, how should I put it, very plump.

"Uh……"

Hmm. This is a bit difficult.

Qing's eyes darted around.

At this, Wang Juhee burst into laughter.

"Since I didn't have a suitable steward to manage the land, I entrusted it
to the Seolga Company, and they keep sending snacks. I didn't want to
eat them, but I felt bad if they went bad after some time, so I ended up
eating them one by one. Ahhh, now look at me."

"Ah."

So everyone had gotten chubby like sparrows before hibernation
because of the Seolga Company.

Of course, the Seolga Company was blameless.

Strictly speaking, the origin of this was the Empress granting
land, wasn't it?

And the Empress had only given a small (small) allowance and
bribe, just in case her daughter was being mistreated.

In the end, going around and around, whose fault was it?

Of course, Qing could confidently assert.

No matter how delicious the snacks were, wasn't it the individual's fault
for not controlling themselves?

"Still, because of this, I don't miss seeing any of the children these days.
Maybe I should have increased my presence earlier."

As a result, she seemed relatively satisfied.

If the Sect Leader is happy, then that's probably a good thing……

"Yes, your Master is eagerly waiting for our youngest sister. You should
hurry along."

After leaving the Sect Leader's hall, a thought suddenly occurred to
her.

The disciples had also generally gained weight.

The Sect Leader had become outright plump.

Then, would Master be like that too?

Hmm, I can't quite imagine it, though.

Qing's steps gradually picked up speed.

From walking, she soon broke into a run.

With a smile on her face, as the familiar, always-open gate came into
view, she shouted in a voice filled with excitement.

"Master! I'm back!"

And so, Qing crossed the gate.

Hmm. No one's here.

Then, creak.

The sliding door opened halfway, revealing a stern-looking noblewoman
who clicked her tongue.

"If you've arrived, you've arrived. Why so noisy and boisterous? Does
my disciple only get wilder as she ages?"

"Hehe. Your disciple has returned."

"What's with the disgusting cutesy from a grown woman? Enough. What
are you doing? It's cold, so come in quickly."

However, Qing just stood there with a subtle smile.

It was a smile that showed a slight disappointment in her large eyes,
with her eyebrows arched in a way that made her seem upset.

It was a smile filled with longing and wistfulness.

Wondering why this girl was acting like a puppy with an upset stomach,
Ximen Surin raised an eyebrow.

Qing giggled and brought up the main point.

"Master? Don't you feel like something's missing? Like a warm hug
with your long-awaited disciple?"

Ximen Surin sighed deeply at this.

For some reason, every time her disciple returned from a journey in
Jianghu, her condition seemed to worsen.

It wasn't a phenomenon seen in her realm, but the insight of a woman
who had been watching over her beloved disciple.

Her disciple's eyes were… off.

The eyes are windows to the soul.

What had she seen to fill her eyes with such rage, with that vicious
killing intent from hatred clouding her natural blue?

Anyway, just by meeting her eyes, it was clear that her inner state was
far from normal.

So, in order to fill that inner emptiness, her childishness, seeking
affection, only increased.

"Come here. You talk too much, as if you're embarrassed or something.
Tsk tsk."

Thus, Ximen Surin, playing the unaccustomed role of a mother, laid her
precious disciple's head on her lap and gently stroked her golden hair.

Having finally succeeded in getting her Master to lie her down, was this
precious disciple or just a troublesome one? Who knows.

"Hehe."

She's happy again, making a fuss.

Then, suddenly feeling self-conscious, she awkwardly sat up and
assumed a polite posture.

"So, did you have a good trip?"

"Yes. Various things happened, but, um, first, this disciple was heading
to Namnyeong. Ah, have you ever been to Zhangjiajie, also known as
Tianzi mountain?"

"Huh."

What a sudden, breathless start to the conversation.

Tianzi mountain?

Wasn't that a den of bandits?

"This disciple was sightseeing there when a bunch of bandits suddenly
attacked, didn't they?"

As expected, no good premonition ever missed its mark.

Hearing ‘bandits' right away, Ximen Surin sighed deeply.

Still, she wasn't too worried, as if something unfortunate had happened,
her disciple's expression, unable to manage her emotions, would have
contorted.

But seeing her bright face, it seemed like nothing major had occurred-

"Since this disciple saw bandits, could I just let them be? So, this
disciple drew her sword and cut off the head of the bandit leader there.
But would you believe it, that bandit leader was actually a master of
the Unrestrained Realm. But who is this disciple a disciple of? Since
Master's disciple is a Transcendent beyond Transcendent, I just went
slash-slash."

"……?"

"Ah. It turned out there wasn't just one Unrestrained Realm Master there.
There was another one called Dora? Doajum? Something like that. But
even with such skill, they were harassing innocent commoners and
committing banditry. So, of course, this disciple punished them
accordingly."

"……?"

"Turns out, it was a whole den of bandits there. So this disciple burned
them all down. Hehe, did I do well?"

Ximen Surin took a sip of her tea.

Something felt very strange about what she was hearing.

"You're saying that this disciple went to the bandits' stronghold, beheaded
their leader, and burned the rest?"

"Yes!"

"Hmm."

Ximen Surin thought, ‘What is this…?'

Honestly, she had no idea what to say. She couldn't even grasp it.

If her disciple was lying, that would be one thing, but she wasn't one to
lie.

But if it was true, for a mere Peak Realm girl to infiltrate the stronghold
of bandits and massacre them… How could the Green Forest be so
easily defeated that their stronghold was destroyed?

"That was a very dangerous thing to do."

"I thought they were just bandits, so I looked down on them a bit. But
they were surprisingly strong. I was a bit surprised."

"Hmm. Anyway, well done. Since they are of no help to the world,
eliminating them is something the world will praise. Yes, so, who knows
that this disciple burned down the Green Forest?"

"Well. The ones who escaped might know?"

"I see. And then, right after that, you headed straight for Namnyeong?"

"Well, on my way there, some soldiers blocked the road."

"No, why is it that everywhere you go… Never mind, please continue
with your story."

Thus, Qing's journey unfolded.

She rescued a Grand Prince in danger and fought against Embroidered
Uniform Guards who had been given some strange Grand Technique.

Then her disciple, feeling that she was lacking, learned a Demonic
Art……

Qing subtly glanced at Ximen Surin.

Ximen Surin let out a deep sigh.

"Let's skip that for now. And then?"

So, she stopped by Namnyeong and found that the Gyelim Sword
School was in danger of being wiped out, so she helped them again.

And then, not wanting to just play around, she moved to Guangdong
and stopped by the Guangdong Jin Clan.

Then the events that unfolded in Guangzhou, the Three Great
Unorthodox Factions, and the Blood Fiend and Blood Cult.

Although the story about stopping by the Gyelim Sword School in
Guangxi seemed like a normal Jianghu journey…

Ximen Surin shook her head.

Whether it was due to her disciple's unlucky fate or the karma of
Heavenly Slaughter that caused disturbances wherever she went, it
was fortunate that things had been resolved more or less well.

Her disciple even showed signs of not being able to control her emotions
in front of her master, leaking the ominous and sinister energy of
Heavenly Slaughter while talking about the Blood Fiend.

It was understandable that she would be upset after hearing such a
story.

And her disciple was commendable too.

"Right and wrong are not something someone else can determine for
you. And it's an incredibly difficult problem. You should do as your
heart dictates, but deciding the direction of that heart is not easy. So,
my disciple, keep pondering on it."

"Yes……."

"But, you learned a Demonic Art?"

The time had come.

Qing carefully observed her reaction and replied.

"It's, uh, called the Samsara Wheel Demonic Art."

Ximen Surin's forehead bulged with a vein, another vein bulged on her
neck, and her fist clenched tightly.

Another one of the Ten Great Demonic Arts Under Heaven!

Seriously, is this bitch trying to collect all the Ten Great Demonic Arts
Under Heaven? How could she pick up only the Demonic Arts that are
notorious throughout Wulin?!

But her disciple's condition was far from normal.

Ximen Surin suppressed her urge to launch a nuclear strike.

She had just returned from hardship, and although she was a bit
foolish, a lot foolish, no, just very foolish, she was still a good disciple…….

"Haaa. Alright. Good job. You did well."

Ximen Surin barely managed to succeed in holding back the nuclear
strike and that very moment.

Qing, of course, had to add a word.

"But Master, even though it's a Demonic Art, it's really convenient.
Look at this. The Sword Force moves on its own, see? Like this! Rotating
Sword Force!"

At this, Ximen Surin's anger, which had barely subsided, surged up
again.

Kwoooooong……!

The mountain birds resting on the roof of the Grand Sect Leader's Hall,
startled by the sudden noise, flew up all at once.