\chapter{Journey to Taiyuan (10)}

Most of the great sayings of Zhongyuan came from the Spring and Autumn Period and the Warring States Period.

This was because the Spring and Autumn Period and the Warring States Period, which spanned several hundred years, were the most brutal periods in the history of Zhongyuan, a terrible era when the world was simply filled with evil.

'Rather, it's because of this that we should not be like this. Please, if we are human, let us live like human beings'. This was the desperate cry of the Hundred Schools of Thought.

There was a bandit named Daozhi.\footnote{A story from Zhuangzhi, particularly mocking Confucius' ideals}

The great Daozhi, the ultimate bandit.

You could easily guessed his character from the fact that he led a force of nine thousand men and still committed theft.

Because in the Spring and Autumn Period and the Warring States Period, a strong army of nine thousand men could easily target a region, or a huge army that could target feudal lords, or even kings.

But what did Daozhi do with a group of nine thousand men?

He just swept the world and committed robberies.

When he was bored, he enjoyed killing people, and giggled at the sight of brothers and sisters, parents and couples fighting and killing each other.

And with a peculiar diet that requires him to eat human liver at every meal, what thief's wickedness can compare to that of Daozhi?

So Sima Qian cried out in anger in the Records of the Grand Historian, saying:

(It must have been very painful to have your amniotic fluid cut off after being falsely accused.)

How did Daozhi die?

It was said that he lived his entire life killing people as a hobby, eating their livers, and when he grew old, he died peacefully among his subordinates, their cries a lullaby.

If heaven truly hates evil and punishes evildoers accordingly, then why did this bastard die peacefully after spending his entire life enjoying killing people without any boredom?

What truly is the will of Heaven? Does the will of Heaven even exist?

If there is, where on earth is the will of heaven!

"Hmm. You bastard."

If you looked at it that way, the sky does nothing.

The numbers that were visible to Qing's eyes right now are just that, and that didn't mean it's forcing her to fill up a few points or to clean up all the evildoers and send them to that hellfire with express delivery.

It just displayed it as a number.

Why?

Hmm. I don't know.

"Young Lady Ximen?"

"Huh."

"What are you thinking so deeply about?"

"Just. What? Is the lecture over? Then?"

Qing pretended to lift her glass.

\textit{Okay, now that the lecture is over, I should break it up.}

\textit{It's hot outside, so I'd like a cool drink.}

\textit{It was mid-May when I arrived in Taiyuan, but now it's late July, and it's so hot that if you let your guard down, you'll start sweating profusely.}

Of course, Qing didn't feel hot at all.

Because Qing gained complete freedom from the heat through the operation of Inner Qi cultivation.

Even in the summer, she wore clothes that are tightly closed around her neck and sleeves. People might thought that she didn't felt the heat, but she actually made her insides into an AC.

The cool chill seeped into the loose-fitting inner garment, with the sleeves and neck tight, and so Qing enjoyed a mischievous vacation all by herself.

According to the scholars of the Hanlin Academy, just looking at a peerless beauty makes your heart race, and if you happened to sit next to her (which was not easy because of the high competition rate), you will feel a truly chilling sensation.

It's actually really cool.

Qing surprisingly blended in well with the Hanlin Academy.

First of all, Qing was a very friendly person and does not hesitate to talk to anyone.

To put it nicely, she's a bit of a brat, but to put it badly, she's a bothersome and annoying girl who never leaves anyone around her alone when she's bored.

And when you looked at the most beautiful face in the world, you could see that she looked so innocent and disobedient that you wouldn't even look at a stingy man, and there is no difference between men and women.

There was nothing particularly special about it.

She like to eat and play, but when she did something, she easily get absorbed and become enthusiastic.

In summary, it's like this.

"Alright! Done! I made it through another day!"

"I held on!"

The scholars of the Hanlin Academy raised their glasses and sing a chorus.

If a Hanlim Academy's bachelor asked Qing, 'Would you like to have a meal together with me?", surprisingly she would easily say yes.

His heart was pounding and his face felt like it was going to explode, but when lunchtime came, the students with the same expressions all followed Qing out.

Unfortunately, he didn't said 'just two of them'.

"Oh, I'm going to get really tired after sitting still for half a day. Don't you think so? I need to stand up and move around a bit every now and then. Kiya, I'm so tired."

Then, Qing tapped the arm of the bachelor sitting next to her with her elbow.

The two scholars' faces immediately turn pale.

\textit{Elbows touch! Elbows touch!}

"Master Yang, Master Yang, but shall we stay overnight? What is it? Aeja, you're a bit careful with your pronunciation. Anyway, what is Gyeom-ae and what is Byeol-ae?"

"Ahem. Humble love refers to love without discrimination, while special love refers to loving those closest to you with a calm demeanor."

"But? Why humility?"

Qing leaned in and asks.

\textit{It smells good, it smells good… …}

Young Master was in a state of confusion!

"Which king would be a better king: a king who cares for those close to him, or a king who cares for everyone equally?"

"Shouldn't you first know if you are close to the king?"

Another bachelor quickly intervenes.

"Well, Miss Ximen. A loyal subject is like a thorn in the mouth, a person who doesn't stumble over something. A treacherous subject, on the other hand, puts on a show and spouts sweet, intoxicating words. So, even if all the kings in the world intellectively urge their loyal subjects to cherish and their treacherous subjects to shun, their hearts inevitably do the opposite. Therefore, a king's favoritism inevitably ends up favoring an incompetent, treacherous subject."

"Is that so?"

"This scholar, however, isn't it inappropriate to use the example of a king for universal love? Universal love is this: loving others' children as one's own, and not loving one's own children more than another's. Thus, a family of universal love is said to be a large extended family formed by several couples who come together and share their children."

The birth of a large family that shares children in this way.

And the extended family is reunited with another extended family through marriage, which is the process of two extended families uniting into one community.

Only when a community of universal love like this covers the world will all the peoples of the world achieve an era of peace and prosperity through universal love.

And what's unique about this community.

Wealth is distributed to those in need, and any surplus resources are not private property. All property is owned by the community, and any surplus is recovered and distributed and recovered again…

"Oing? Isn't it a little red…"

"What's interesting is that Mohist disciples were all masters of the art of water. So, despite being scorned by many monarchs of their time, they managed to maintain their bizarre community."

The thinkers of the Hundred Schools of Thought are not just talkers of learning.

Each and every one of them was an outstanding general, a leader of a military group.

In particular, the Mohists believed that the ultimate means of preventing war was through water fortification and defense, so there is a theory that the Tulou, a fortified public housing construction technique of Zhongyuan, originated from the Mohists.

No private property, no favoritism, small communities starting from the community.

And the large community, which is a gathering of those small communities.

And space defense… … .

Doesn't that feel a bit, terribly unsettling?

In fact, Qing is a Korean who received a higher education.

Studying the thinkers of Zhongyuan?

I'll fight back with a nosebleed!

I've had that thought before.

However, the collection of the Hundred Schools of Thought, which is a compilation of all the thinkers of the Spring and Autumn Period and Warring States Period, has over two hundred thinkers.

So, if the Qing were to finally launch a counterattack and say, 'Who said something like this in the faraway Western Regions?', wouldn't everyone say, 'Oh, that's what the sages who are so-and-so have said', and that it was something that had always been said? Wouldn't one word from the Qing be countered by three or four others?

Everyone's three or four words add up to hundreds of words.

Well, I don't know.

As expected, the population is a gangster.

They say people's thoughts are all the same, so I thought that the person on the other side of the world had the same thoughts here at least once.

Just look at the case of Taoism (Confucianism).

Pure Tao is a state in which all artificial things are excluded, and this is a concept that's almost identical to the idea that Mr. Kojeng P of the Western Regions mentioned.\footnote{Kojeng peul means 'nosebleed play'. Couldn't find which philosopher it meant to}

Thus, the way of inaction and nature is natural even if people do not know it, that's, it corresponds to good, so the politics of the wise man is natural, it's so natural that one should not even know that someone is ruling… …

Anyway, after bringing it up for no reason and getting a wake-up call, Qing doesn't bring up the topic of the nose so carelessly.

What is this superhuman that Master Ni of the Western Regions is talking about? \footnote{Nietze}

Should I live like a pure child?

Ah, speaking of virtue. Lao Tzu said that a person with deep virtue is like a child. So, Master Ni also studied the Tao Te Ching?

But individual perfection?

So, what did you call that individual superhuman? The will to power? Even if he transcends that and reaches the superhuman, what does that mean?

If people do not attain the Way and benefit the world, then what is the need for such a superhuman being in the world?

Conversely, if the world does not transcend together, what is the point of waiting for a single superman?

Then what would Qing have to say?

\textit{Why are you asking me that?}

\textit{Since they said that, you should ask that person, why are you saying that to me?}

It's really a mess, really.

In fact, the reflections of the big nose people tend to be too focused on the individual.

What comes to mind is that the professor said, half-jokingly and half-seriously, that if someone tried to influence society beyond the individual level, the church's heresy judges would have hung them and burned them at the stake.

He said it was a curse of the real God.

There is not much to describe him.

Above all, because the Qing are also of the same ethnicity, they have no emotional sympathy at all for a society of individual subjects in which each individual becomes the whole, complete on their own.

\textit{So, oh, oh, I just heard it in passing, so I don't know for sure.}

\textit{Shit, you should have entered the martial arts world too, but I'm a bad student so I have nothing to say…}

Still, Qing is steadily accumulating knowledge.

"Oh, I don't know. Come on, drink, drink!"

Of course, knowledge is not embodied as wisdom, so what good is it to cram all the precious items into a warehouse?

It's like just shoving everything in because it's good without even knowing what it's or where it's used.

Organizing the warehouse seems like it will be a long, long time coming, so it seems like there is nothing left to do in life.

Anyway, after drinking and eating like that and coming back, she suddenly find Tian Yuxue groaning in the basement of the mansion, holding a map.

"Master, I'm here."

"Are you here? Go to the herbal bath over there."

Tian Yuxue answers without even looking back.

Two months have passed, but Tian Yuxue was still interpreting the treasure map.

It is not an incredibly grand task to interpret the treasure map.

At first, it was a bit grandiose, so he deciphered the code and drew a map by matching it here and there, but the problem started after that.

By looking at some maps drawn as narrow areas without place names, you have to figure out where the village is located in this vast central land.

How?

Comparing them one by one.

Originally, a detailed map of Zhongyuan was something that was treated as top secret by national law, but the original Divinie Thief were thieves (plus aspiring thieves) who didn't care about national law.

Even if you only looked at all the different types of Zhongyuan maps attached to the basement, you can't escape the punishment of a great sinner.

So, even if you don't know where to accumulate treasures, you have to manually find the location of the treasure by holding up a small piece of map and comparing it to the entire Zhongyuan.

Either way.

Qing, who was soaking in the medicinal bath, notices that the water has become transparent and called out to her teacher.

"Master? It seems like the medicine has completely worn off."

"Already? There's no way it could have come this quickly."

Qing was not only fast at eating.

Starting shortly after arriving in Taiyuan, once every two weeks.

This is the fifth Flowing Flex training in Taiyuan in just over two months.

It was a training method that's difficult for the master and painful enough to kill the disciple, in which the joints of the limbs are gradually bent beyond their limits, thus increasing their limits.

But instead, with the wisdom of the Qing, she uses the parasite inside her mind to absorb the pain.

It could be said that's why Qing still maintained a strong respect for her Master.

"Oh my, I'm going to fall, I'm going to fall."

Tian Yuxue, who had finished his disciple's joint manipulation, lay down inside the stone chamber, panting.

Qing, who had been drooling profusely with her eyes wide open, suddenly regained focus and looked around.

\textit{Oh, I guess the training is over.}

\textit{My whole body was numb and there wasn't a single spot that didn't hurt, but I guess I should be satisfied with this since I can just blanked out for a bit and come back up and the torture will be over.}

Qing, who was tied to the oil tank, might seemed just wriggling around, but then she skillfully escaped on her own.

After the sixth procedure, that's, after the Flowing Flex reaches the 6 star, it's possible to get out on your own as long as the device is not too tight and the joints are not broken.

Now, there is no longer any need to look longingly at the exhausted teacher and cry out for help between the minimum human dignity and the limits of one's bladder.

"How about the map?"

"Hahhh, there's not much left. Just a few more days to find the right spot, and that'll do. We need to have all the candidate sites selected by August so we can check them all out."

Great Study Hall was also closed in August.

That's exactly why Tian Yuxue invested all his spare time in the map-matching game.

If he pinpointed all of the candidate sites by August, they can go out to find the treasures recorded in the treasure map.
