\chapter{Journey to Taiyuan (2)}

Since childhood, Lee Cho-soo had been feared by everyone due to his exceptional talent that transcended common sense.

Thus, people held him in awe and called him, Tattletale, Tattletale Lee Cho-soo.

When Lee Cho-soo tattled, his face would be filled with such utter and complete injustice that it seemed as if his intestines would burst and his liver would explode. And his voice would carry the desperate lament of the most wronged person in the world, a sorrowful cry that echoed throughout the entire world.

So, when someone heard Lee Cho-soo's appeal, they would find themselves thinking, Ah, this fellow is truly wronged. This is the expression and voice of someone who speaks only the truth. How could such a thing happen in this world?

The listener would be unknowingly persuaded, empathizing with his sorrow.

Then, the events of the past would be twisted, making Lee Cho-soo the only innocent and blameless person in the world.

And everyone else was the perpetrator.

How could the world give birth to Lee Cho-soo and also such a cruel reality? Such a reality should not exist. I must help this poor soul. This was the train of thought that would naturally follow.

It was a terrifying talent, one not allowed to humans, to twist the cause and effect of the past with human power.

And this talent was directed at the Supreme of the Wicked Path, the revered leader of the wicked youths, the beacon and guide showing the path that the Wicked Path should take, the Lord of the Wicked Path Alliance, Bu An-pyeong.

"Lord! I am so wronged, so wronged, I, hic, gasp, I can't, I can't breathe, I'm sorry, hic, just the thought of that bitch, I feel so wronged that I can't even breathe, hic!"

At that, the pretty young man sitting in the highest seat, with his delicate and rounded features, furrowed his brows.

"What? Why is a perfectly fine fellow acting like this?"

"Lord. It is known that when one experiences great mental shock, symptoms such as difficulty breathing can occur."

The one who spoke up beside him was First Under Heaven, Sun Woong, the master of the Nang-Go-Gak of the Wicked Path Alliance, and the person in charge of the overall affairs of the alliance.

"Tsk tsk. Men these days are so weak-minded. It's all because of a lack of spirit. Everything should be overcome with mental strength. Mental shock? Mental shooock? Why are the young ones these days lacking in spirit? In my time, I had my bones set and my meridians cleared with nothing but spirit. Talent? Elixirs? Divine Arts? They're all useless. With only spirit alone-"

"Lord, why don't we first hear what he has to say?"

"Ahem, have I acted like a nagging old man again?"

"Yes. You have."

"It's all for their own good, you know. It might not be pleasant to hear, but it's all golden advice that will strengthen their bones and flesh. As I've aged and reached my realm, I feel pity and heartache when I see those struggling below me."

"You did it again. For now, please close your mouth and continue listening."

"Fine. So, who is this bitch?"

"The Sword of Heavenly Blossom! It's that bitch, the Sword of Heavenly Blossom!"

Thus, Lee Cho-soo poured out his grievance.

The Sword of Heavenly Blossom had appeared in Guangzhou, a vicious and cruel woman no different from a Heavenly Slaughter Star. (True)

At first, she hid her true nature, pretending to be a shaman and concealing her identity while gaining popularity, thus hiding her wicked disposition. (True)

And then, she finally revealed her tyrannical nature (True), suddenly attacking the Guangzhou branch, causing a massacre. (True)

"You wouldn't believe how cruel she is. She collapsed the entire building and then stood there, smashing the heads of the escaping members one by one like she was playing whack-a-mole! How could such a vicious woman exist in this world!"

And finally, it seemed that even pretending to be a shaman had become tiresome for her.

How could we make Guangzhou more prosperous? How could we contribute more to the Wicked Path Alliance and play a part in the unification of the Wicked Path under Heaven? As these thoughts troubled the Branch Strategist and the Branch Leader, who were having a drink together (False), she suddenly ambushed and killed them.

"How dare that bitch kill our Branch Leader, sob, even now, just thinking about that bitch makes me, hic, hiccup."

Lee Cho-soo's face turned red, and eventually, he shed hot tears.

If one were to describe his tattling, one could say that it had reached a level of art that could not be ignored, a realm beyond human.

To this, the Supreme of the Wicked Path responded.

"Well, why is a grown man crying? Listen carefully. A man cries only three times in his life. When he is born, when his parents die, and when he loses his sect."

"Lord."

"Ah, did I do it again?"

"It's not that. If he lost his Branch Leader, isn't it the same as losing his parents? Isn't it okay to cry then?"

"Ah. Is that so? Hmm. Anyway, if what you say is true, she's not someone we can leave alone. It's one thing for the young ones of the Orthodox Faction to cause a ruckus, talking about eliminating evil and upholding justice, but to directly tarnish the reputation of our wicked youths, we can't let her live."

It seemed that even the great Supreme of the Wicked Path couldn't help but be swayed by Tattletale Lee Cho-soo's history-altering abilities.

However.

"But how dare she harm a strategist of the Wicked Path Alliance? When smart ones are already so rare?"

"Um. Lord? Bang Jeom-myeong is still a normal strategist, and he woke up fine this morning?"

"Hmm? What are you saying? He said he's dead. Said the Sword of Heavenly Blossom ambushed him and stabbed him in the neck?"

"Bang Jeom-myeong has been staying at the Nang-Go-Gak for almost two months now, eating and sleeping there because of the Wulin Tournament. I told you he woke up this morning, not that he went to work."

"Isn't there another strategist with the surname Bang?"

"He's the only one with the surname Bang. And Strategist Seong, who was sent to Guangzhou, is a Senior Strategist. And what's this about a chest of elixirs? Did Lord perhaps send them with your personal funds?"

"I didn't do that? Did the General Manager send them?"

"I didn't either. Where would I find elixirs to send, not just one or two, but a whole chest?"

"Then, where is Strategist Seong? Where is he?"

"Isn't he in Guangzhou?"

Only then did the two's gazes turn to Lee Cho-soo.

"You, what the hell?"

"Lord?"

"Lock this bastard up for now."

"Lord!? There must be some mistake, I'm innocent, I'm innocent! I only told the truth as it is, Lord! Lord!"

Lee Cho-soo was dragged away by the martial artists of the Wicked Path Alliance.

"But, regardless of what happened, we can't just leave that Sword of Heavenly Blossom alone, can we?"

"No matter what the circumstances, if word gets out that she single-handedly defeated three minor sects in Guangzhou, how will the world view our wicked youths?"

"That's right. You know how it is. Once people start looking down on you, all sorts of riffraff start coming at you. I'm already annoyed by those upstarts making a fuss about being the next generation or whatever, upholding justice and whatnot. If we let this go, every Tom, Dick, and Harry will start acting up."

"So, what will you do?"

"We don't know where the strategist we supposedly sent is. The strategist we didn't send is at the Nang-Go-Gak, and there's talk of a chest of mysterious elixirs arriving. Don't we need to find out what's going on, regardless?"

"I will dispatch an investigation team."

"Not just dispatch, we'll go too. I have a bad feeling about this. I need to see and judge that Sword of Heavenly Blossom with my own eyes."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

However, that Tianhuajian was not in Guangzhou.

By the time the Sword of Heavenly Blossom left Guangzhou at the end of the intercalary month and arrived at Zigui County, where the Seol Clan Merchant Group was located, it was already early April, with March having passed.

However, for some reason, the weather was getting colder as spring deepened.

This was because they had moved north to the cold continental climate, due to the vastness of Zhongyuan.

Thus, a huge six-horse carriage traversed Zigui County.

Unlike the interior, the exterior was black and undecorated, giving off an eerie and imposing aura.

This was also why they hadn't encountered even a single bandit on their way here.

It was because the carriage looked so ominous that it seemed like it would spell doom if they carelessly touched it.

However, strangely, in Zigui, people smiled or grinned upon seeing the carriage.

The gates of the Seol Clan Merchant Group were wide open even before the carriage appeared, and when Qing got off, a familiar face was right there.

Qing jumped off the carriage and flew into Choi Leeong's arms like a cicada clinging to a tree.

"Gramps!"

"Hey, you brat? What are you doing in front of outsiders, you grown woman?"

However, Choi Leeong's words were not persuasive at all.

Since he was grinning from ear to ear, anyone could tell that the old man was more thrilled than anyone else.

Choi Leeong carried Qing and immediately headed to the dining hall.

It was a natural flow, as if it was obvious, even though he hadn't even asked if Qing was hungry.

"Where's that Xue bastard? Is he still in Chang'an?"

"Don't even mention it. He's thinking of naturally dying and disappearing these days. The pressure from the marriage talks is getting to him because of that Young Master's noose, so it seems he's having a hard time."

"Ooh. That Xue bastard. A seductive beauty."

"Even with the influence of the Greatest Merchant Group of Shaanxi, he's somehow managing, but if the authorities start to really pressure him, what can he do?"

"Huh? The Greatest Merchant Group of Shaanxi?"

After Qing swept through Chang'an, the immorality of merchants became a major topic.

Until then, it was thought that merchants were just like that, that they were human trash who sold their souls for gold and silver, so it was natural for them to act atrociously.

But Qing's enlightenment swept through Chang'an.

Merchants grow large because customers care for them, but once they become big merchants, they look down on customers as if they were servants or slaves without a second thought.

Why do you just take it?

If you don't buy their goods, cut off transactions, and actively inform others of their wickedness, they'll go out of business.

The Great Hero Under Heaven, Zhongyuan' First Beauty, and the one who suggested a new history of commercial ethics, the Incarnation of Righteousness's great guidance, was a true teaching that awakened people.

As this teaching spread, there was one merchant group that showed its true worth.

The Taiqing Merchant Group!

It was a bizarre organization where a majority of its members did good deeds purely for personal reasons, which could be described as selfish altruism.

Aside from major projects like relief (but only if you memorized the doctrines of the Divine Cult) or free schools (but with the doctrines of the Divine Cult), countless minor acts like helping an old person carry their luggage, guiding a lost child, or cleaning the streets piled up, eventually creating a huge wave.

Everyone in Chang'an, please use Taichung Merchant Group's goods!

Everyone in Xi'an, please use Taichung Merchant Group's goods!

Everyone in Shaanxi, please use Taichung Merchant Group's goods!

What's that, you? Didn't you just come out of a Jangryeongbang store? Don't you know that Jangryeongbang is a business established by the son of Jangheung Merchant Group? How can you buy the goods of such scum? You're so shameless!

What? You're saying you buy these dirty merchants' goods just because they're a few coins cheaper? Don't you know that using Taichung Merchant Group's goods contributes to relief projects, our children's schools, and subsidies for half-priced physicians?

A form of nationalistic consumption, which would have been common in Qing's hometown, appeared in Zhongyuan, transcending hundreds of years of time.

But that wasn't all.

Look here, sir. It's not just about being a little cheaper. Taichung Merchant Group's goods are well-made, of high quality, and the management of food and grains is thorough and trustworthy. Even if there's a problem, they take responsibility and handle it, so isn't it much more beneficial than saving a few measly coins!?

This was because the purpose of the Taichung Merchant Group was not to generate profit.

However, from the customers' point of view, how could there be such a kind merchant in the world? If an outsider heard, it would sound like utter nonsense they would never believe.

The Taiqing Merchant Group developed at the speed of light.

Thus, the Greatest Merchant Group of Shaanxi. The Taiqing Merchant Group.