\chapter{Journey to Taiyuan (11)}

Last June.

In Taihe County, Jiangsu Province, a martial arts competition was held where 50 million (estimated by the Heretic Alliance\footnote{邪道聯; Xiedao Lian;Sadoryeon}) of Apostles gathered and united their hearts.

The next generation of the Heretic Alliance will be led by the Heretic Alliance's later leaders, and the honorable juniors of the Heretic Alliance's ten dragons will be chosen.

They also held a ceremony to launch a new signboard and intermediate base for the Southeastern Vicious Tyrant\footnote{邪覇;Xieba;Sapa} factions, which have been growing in power recently.

They also collectively condemned the Orthodox Wulin, saying that the martial arts world only worships the martial arts, and that they try to deceive the masses by blurring the true nature of the martial arts world as swordsmen through other political factors, such as agreements.

Of course, unlike the Orthodox Wulin's competitionn, this was an event with almost no onlookers other than the participants.

Since it was a martial arts competition of the Orthodox sects, there was no way that the general public would be harmed by it anyway, so it was an event that was overflowing with tourists from all over Zhongyuan.

You're asking to be a spectator in a city where all the world's evildoers have gathered?

People would think there's something wrong with your brain.

There was also a rumor that during the entire Xiedao Lian Wulin Competition, parents of daughters from Taihe were put on high alert, and that they were kept tightly hidden and not even allowed to leave the house.

And this festival of the Apostles' sons gathered all that heat, and at the 'Telling the World of Martial Arts' event, the spirit of the Apostles' sons was raised with words they wanted to say to each other.

And the person who became the talk of the town in this world of martial arts was Wang Daeyang, the third son of Lulin Chaeju.

First of all, his appearance was unusual. He appeared wearing yellow mourning clothes and carrying a large flag hanging from a long pole behind his back.

So the four letters on the flag.

賣身葬父!\footnote{Mai Shen Zhang Fu; Selling oneself to bury one's father}

This was a saying from a long time ago, long ago during the Han Dynasty, to be exact, from a famous filial son named Dong Yong.

Although Dong Yong was a very filial son, he seemed to have no ability, and his family was unable to escape poverty.

Then, when his father passed away, Dong Yong went to a rich family and sold himself as a slave to pay for the funeral expenses, and held his father's funeral.

Perhaps, his father in heaven was looking down on his son who sold his body to pay for that funeral and shed tears of blood.

If he was smart enough to think like that, he probably wasn't poor enough to sell his body to pay for a funeral.

Anyway, Dong Yong, who was ignorant and incompetent but had deep filial piety, held the funeral like that.

Well, it's said that he ended his life as a slave thanks to the Jade Emperor's daughter who was impressed by his character and helped him.

It means that a fool of that level of stupidity has no answer unless someone like the Jade Emperor's daughter comes forward.

In any case, selling one's own body to pay for one's father's funeral was a noble act, the pinnacle of filial piety.

For your information, this filial piety, the fact that old parents, even after they die, held back their living children with funerals and three-year mourning, was the very culture of filial piety in East Asia, a proven ruling tool that keeps the common people as common people.

But this was the Heretic Alliance's Wulin Competition.

What kind of virtuous man was doing in a place where the world's most unfilial sons have gathered?

"Everyone, I must confess to you a terrible and shameful thing! The Green Forest, the Green Forest has been defeated! We have fallen for the tricks of that detestable Heavenly Blossom Sword, that vile and cowardly woman!"

Surprisingly, there was not a single lie anywhere.

Is it miserable and shameful? Yes.

Was the Green Forest defeated? Yes.

Is the Heavenly Sword evil and cowardly? Yes.

The apostles gasp in awe at that astonishing truth.

What?

Now-twenty-one, a woman who was twenty at the time killed Wang Cheol-jun, and on top of that, she even beheaded and burned the famous Do-woo-sam, a master of the Green Forest (to the Sapa)?

Does that even made sense?

It was the job of the Heretic Alliance's strategist to made it make sense.

So, a story unfolded that made everyone unable to endure extreme anger.

One day, Heavenly Blossom Sword, a woman from the Orthodox sect, appeared and was introduced as his lover by his eldest brother.

However, unlike the eldest brother who showed pure and innocent love, Heavenly Blossom Sword looked at the second brother and Dowoosam with impure eyes.

And the wicked woman sowed discord among the brothers and lured Do-sam into her skirt and played with her as she pleased, causing a great disaster by poisoning the well.

The chieftain, who saw the brutal murder of his daughter, collapsed on the spot.

His eldest brother believed in the Heavenly Blossom Sword, so he introduced it to the second brother, and from that meeting onward, they just met each other, had fun times, and hung out together. But Wang Daeyang had an ominous feeling about where that meeting went wrong…

And so, at the moment when his family was completely destroyed by the evil woman, Wang Daeyang cries out in anguish, shedding tears of blood.

-Why! ​​Why would you do something like this!

Then Heavenly Blossom Sword just laughs coldly.

-Well. A hero who conquered the Green Forest, wouldn't that be cool? You apostless are nothing but a rug for my reputation.

-Just for that reason!

Wang Daeyang took up his sword to seek revenge.

-Young Master! Young Master must survive!

-You must reveal this truth and punish that wicked witch! Family Head! Please, Family Head!

-No! Let go! Let go!

The story ends with the subordinates rushing towards Heavenly Blossom Sword even after knowing of his death, and the desperate screams of Wang Daeyang as he was dragged away by his subordinates.

'How can there be such a vicious woman in the world!'

Most of the reactions were like that.

There were a few reactions like, 'But is she really pretty?', but the story of the destruction of the Green Forest, which was 'reasonable' according to the Heretic Alliance's strategist, had to be told in that way to make sense.

Or what, did the little girl, who was only twenty, attacked head-on, killed two Unrestrained Realm Masters, cut down countless bandits, and then brazenly set fire to them?

"Therefore, I earnestly request this of you, the Heretic Alliance! If you take care of the Heavenly Blossom Sword, I will sell my body. Whether you treat me as a slave, take me in as a godson, or take me as a son-in-law, I will follow you for the rest of my life!"

That was when.

Wasn't that the Apostle who was sitting on that high platform clapping his hands?

It was the sound of applause that contains enormous internal energy, ranked third among the ten greatest masters in the world, first in his opinion, and first among the Heretic Alliance member.

Clap! Clap!

No, what kind of applause was this?

The Six-Combinationsm Full Bloom was a technique that's considered the ultimate in sound transmission, allowing sounds to be heard clearly right next to you, as if whispering from all directions.

It was called the Six Combinations because it's a voice heard from six directions simultaneously: front, back, left, right, up, and down.

The applause from that high and distant throne was heard clearly, as if whispering from all directions, in the ears of everyone present.

What a truly shocking revelation!

Moreover, the voice of the Heretic Alliance Leader, though not loud, resonates clearly to everyone.

"I can't help but admire your filial piety. However, since you haven't yet dealt with your enemy, you can't be called a filial son."

The apostle pauses for a beat and then continues speaking.

"If you strike down your enemy and bury your father, wouldn't that be the kind of act that moved Heaven and granted you help, as seen in the story of Dong Yong in the past? Therefore, seeing your sincerity and filial piety, I will dedicate myself to helping rebuild Lulin! This was a promise I make in the name of Fu Anping\footnote{傅安坪;Bu Anpyeong}!"

The Unorthodox warriors were greatly shocked by this.

If you kill Heavenly Blossom Sword, you can use Wang Daeyang as your servant.

If you defeat Heavenly Blossom Sword, the first apostle will help rebuild the Lulin.

The slave's property was the master's property.

In other words, you become the master of the Lulin!

The moment when the Apostles' tilted their head in confusion, wondering, 'So what if the Cheonhwa Sword was vicious? Isn't it the victims' fault for being idiots?' a giant exclamation mark appeared above their heads.

The last resort was to kick the butts of the Unorthodox bastards who can't move with just a story!

There's even a justification for prioritizing filial piety!

The apostles suddenly became desperate and looked at each other with mean expressions.

Fu Anping looked at the crowd from the top of the altar and said something in a small voice.

"Look here, Chief. Why has the crowd thinned out so much? Did everyone go home already since the Heretic Alliance competition was over? Didn't you send a notice telling everyone to stay in their seats until the end?"

Clearly, when the martial arts competition was held, the square was filled with a tightly packed crowd.

Now that he looked at it, it's shabby, the gaps between the crowds are wide, and there's no one at all at the end of the square, and the difference in the number of heads was clearly large.

"I sent them, but didn't they came after leaving only some men behind? In fact, leaving their turf empty for so long would be a burden."

"Tch. This was how unity works. Unity. Those Orthodox bastards stick together no matter what, but why are we always just concerned about our own interests?"

Fu Anping grumbled.

But Chief Secretary Sun-woong's words also make sense.

Unlike the Orthodox guys who can go anywhere without worrying about leaving, the Unorthodox guys became more anxious the longer they are away.

And a few days later, in early July, the Heretic Alliance martial arts tournament ended with a closing ceremony.

For reference, the final event of the closing ceremony ambitiously prepared by the Heretic Alliance, which was proposed by the Heretic Alliance Supreme Leader Fu Anping and moved all the executives to tears, was as follows.

'Biting into a white peach, I gather my resolve to dedicate my body to the world!'

What was a peach?

It was the symbol of loyalty, and a magnificent loyalty, in Zhongyuan, starting from the Peach Garden Oath.

This means that all of us in the Heretic Alliance, followers of Heretic Path, are united as brothers.

There's a white peach, as the metaphor for the white path!

This was also an expression of the grand will to devour the white path Wulin, or the Orthodox sects.

It was a truly great ceremony that revealed the apostles' unity and ambition in one fell swoop.

If Qing knew, \textit{oh, I think I know that}.

\textit{Didn't even the two-letter English company hold a ceremony of climbing to the top of Samsung Mountain and eating an apple?}\footnote{LG, although there's no recorded news of that written in English}

\textit{It's like pledging to bite the Apple while keeping Samsung underfoot!}

\textit{I guess I ended up just having fun and falling asleep.}

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Men always say.

'I don't even want a peerless beauty like Seo-shi. I just want to be friends with a simple woman who I can communicate well with and live comfortably for a hundred years.'

Of course, this was not at all simple.

This was especially true for the bachelors of the Hanlin Academy.

First of all, looking at the current situation where Confucianism has fallen out of favor with the Imperial Palace and been banished to Taiyuan, the future of the Confucian scholars here was not so bright.

If Qing had been even slightly knowledgeable about Chinese history, she might have recalled a peculiar historical event in this martial arts world: when Emperor Gaozu burned Mencius, no one stopped him.

This was an incident where Emperor Gaozu became furious at a passage while reading Mencius.

It was just one line: 'If the king treats his subjects with contempt, the subjects will treat the king as an enemy.'

Why are you angry at such an obvious thing?

Well, he's the emperor.

Even if the emperor was bored and burned, tortured, and killed his subjects' families, the subjects must love the emperor as if he were their own father.

That is, it's because the emperor insisted that even if he was the lowest of human beings, he must be respected absolutely and unconditionally.

Of course, this was the basic level of consciousness not only of the late Emperor, but of all rulers of Zhongyuan up to now, and of future leaders as well.

Anyway, the future of the Hanlin Academy graduates was not so bright.

There are only lines there that said that you have learned something in your lifetime.

That means, even with that simple, easy-going woman who was like a friend for a hundred years, they had nothing to say other than the words of Mencius, Confucius, and the sages.

And they said they didn't expect anything less than a poem, which was a roundabout way to say they didn't say it was okay if she was ugly.

This means that if you were as smart as Zhuge Liang, you wouldn't be a great man who would take even the world's most ugly woman, Huang Yueying, as his wife.

So, the ideal type of the scholars of the Hanlin Academy was actually something that has only been around for a very short time throughout history.

At minimum, it's Chai Yan\footnote{Chinese poet from Three Kingdom's era}.

There was no specific record of Chai Yan being a beauty, but considering that she was a devilish woman who captivated countless men in her life, isn't it common knowledge that she was no ordinary beauty?

And if they had been given another option?

Ximen Qing was right there.

She was a fairy who truly pierced the hearts of the scholars of the Academy.

She listened carefully to the boring scriptures.

Not only did she listened, but she also responded with a hint of admiration, saying, 'Wow, you're so smart'.

There, she has a lively demeanor that brought smile to your face just by looking at her, and she readily approached and extended a hand to timid students who would otherwise just rolled their eyes if not invited.

The only downside was that shes so pretty that it makes them felt inferior.

If she looked just average, they would have tried to gather courage, but because she had such transcendent beauty, they were a thousand times more vulnerable.

After the morning lectures at the Academy, an even more intense lunch lecture took place at lunchtime.

It's a competition to see who could tell the more interesting story to Heavenly Blossom Sword.

"Young Lady Ximen, do you happen to know the expression ‘seojaseoajjaa'?"

I don't know.

"There's a saying that goes, ‘It's useless to use it.'"

First time hearing this.

"Do you know the story of the Tanglangpo ship? It was…"

Of course I don't know.

However, Qing thought.

\textit{Why do these guys keep making me talk while I'm eating lunch…}

\textit{Still, it's not boring to listen to because it's a story I'm hearing for the first time.}

The kind-hearted Qing listened to all such stories.

Of course, it was also beneficial for Qing since everyone else seemed to be too busy talking to eat.

However, it seems that people with bad personalities did not want to hear about studying at the dinner table, which would ruin their appetite.

"What, you brilliant scholars, do you even eat instead of talking? Are you only talking about noble things, like a restaurant or a collection of scriptures? Huh?"

Like that.
