\chapter{Journey to Taiyuan (9)}

The Hanlin Academy was not a place for women.

Well, there are many maids working and many ladies in charge of the kitchen.

If you ask if there are any female bachelors?

That's not it either.

Occasionally, they held exchange meetings for female writers, and former royal court ladies held classes for women who aspires to become ladies.

However, the request to create a space for women in the Hanlin Academy Taehak lectures was a somewhat different story.

"Scholar of Study, I understand your concern for your students, but isn't this unprecedented? Of course, it's within the master's discretion to allow them to listen to the lectures during their stay."

The Great Scholar, the most senior member of the Academy, expressed his displeasure.

'Listening to a lecture' meant you were just asked to sit quietly in a corner of the lecture hall and listen with your ears.

In the Great Study Hall's lectures, everyone had their own topic and interpretation, and everyone who listens added their own interpretation to it, and through discussion, they gradually expanded the words of the sages and the concepts of Confucianism.

This was an academic activity that taught young scholars (not in terms of age, but in terms of learning) while gradually expanding the scope of Confucian teachings.

Asking to include someone who is not a member of the Academy?

And a woman who's not even a man?

She's not even a scholar.

It's a vague and ambiguous statement to say that she started with only a few Buddhist and Taoist scriptures and learning.

If you read the Buddhist scriptures once, that's what those in elementary school level could do, so Qing he was roughly a child with the intelligence of a six to ten year old by the standards of the Hanlin Academy.

This may sound unfair to Qing.

Still, you could say that she read so much Taoist and Buddhist scriptures, but it wasn't academic, it was just recitings.

But, this is the Hanlin Academy.

If we draw comparison with martial arts terms, it's easy to understand.

Let's say there's a place where masters of the highest level gathered and exchanged advanced martial arts principles beyond swordsmanship.

What if a third-rate warrior showing up there?

It wasn't even a martial artist, but a famous scholar from the Confucian world appeared and wanted to discuss martial arts.

What, are you saying his level is too low? Then it's like asking if what he learned was literature and not ignorance.

So, with Qing interference, it's natural that the scholars of the Academy feel bad.

The youngest prodigy of the Orthodox sects, the famous Divine Dragon?

That's a story about Wulin.

But this is Yulin.

Who was Tian Yuxue?

He was a lecturer at the Hanlin Academy Academy and was a Great Man who is undoubtedly the best in the world when it comes to giving lectures.

He was a great scholar of the time, whose eyes shone brightly as scholars of the world seek even a single word of teaching from him.

A giant like that suddenly brought a martial artist and declared her as his favorite disciple?

Suppose the greatest martial artist in the world, Master Wunue, suddenly brought a Confucian scholar who had only learned third-rate swordsmanship and declare him as his successor.

How would the martial artists felt?

Tian Yuxue opens his mouth again.

"Yonggan, listen to me."

By the way, Yonggan here is a polite term.

"The human heart cannot be impartial, so honestly, I'm more drawn to my beloved disciple. Isn't that the karma of being born human? However, there's a difference between caring for your beloved disciple more than your own and using your disciple for your beloved disciple's sake. I'm not that kind of a worthless person, am I?"

He said that he would be more or less frugal, but he would not exploit or exploit other disciples.

The Great Scholar nodded his head to him.

"Wouldn't I spend half my year wandering the world, observing how things turn? I guarantee you that if that child, Qing, participates in the lectures, everyone will benefit, and if we achieve great things together, there's no harm done, wouldn't it?"

The Great Scholar raised his eyebrows.

"How could that be? It's only natural for a man to covet a woman, and being a scholar doesn't mean he's not a man. If a woman joins the discussion of Confucianism, the man's passions will naturally follow suit. Human passions are finite, so if you focus on one thing, you'll end up neglecting others. I'm worried that everyone will neglect their studies because of this."

"That may seem like it, but trust me and just wait and see."

"Ahem. That's because this has never happened before. Doesn't Scholar know what the precedent is?"

Whoever took action first and left a record of it in history makes it easy for others to follow suit and make excuses.

"Besides, I heard she's the candidate of the best in Wulin? She's also renowned for her beauty, even among women. I don't understand what Scholar of Study is thinking."

"Then let's try it for just one week. Great Scholar, please observe. If you decide it's interfering with my lecture, I wil not make any complaint."

"Hmm. If that's what Scholar says."

The Great Scholar nodded with an arrogant expression, like a scholar who had been told to try some poison, with a look of utter distaste.\footnote{Socrates}

So, after eaten a hearty breakfast, Qing stood on the Great Study Hall podium and looked at the students.

\textit{I ate a big breakfast for no reason. Even though my body has superhuman digestive power, I feel like I'm going to feel full.}

\textit{Somehow I feel like not everyone is looking at me that kindly.}

"Come on. Be quiet. This is my beloved disciple, Ximen Qing. It's a bit sudden, but since you're studying together this summer, shouldn't you pay your respects?"

Instead, confusion spreads.

"Elder? Your beloved disciple?"

"If you're talking about Ximen Qing, could she be that Ximen Qing? I heard she's a young expert who's a disciple of the Zenith Among Women."

"Ah! Three-Headed Beauty! I think I've heard of it before!"

The expression on her face suddenly turned sour.

\textit{That damn three head title won't go away.}

In any case, inside the Great Study Hall, a place for conversation opened up where everyone was gossiping with everyone else.

Qing looked back at Tian Yuxue.

'Is this okay?'

'There's no sense of order at all.'

But Tian Yuxue only slightly raised the corners of his lips and said this.

"Okay. Say hello to your seniors. Oh. So, you're planning on not showing your face to the seniors you'll be studying with? It's the way people first meet someone, and that impression stays with them for life. So, do you intend to remain a woman who hides her face and can't be seen?"

\textit{Hmm. I'm not sure if this is right.}

\textit{But since Master seems to have a plan, I'll just do what I'm told.}

Qing pulled down the veil.

And time stopped.

The interior of Great Study Hall was silenced in an instant, as if it had been paused.

This is the moment when the harmful beauty that everyone, except for a few with a certain taste, unanimously praised as the best beauty in the world, is revealed without any concealment.

"Hello. I, Ximen Qing, the person of Wulin, send my greetings to the scholars of the Confucian world. Although I am young and lacking knowledge, I have been told that it's not shameful to not know, but rather to not seek to know is shameful. Therefore, I ask you, my seniors, to provide me with much guidance."

"Oh, it's the story of Confucius and the Heavenly King."

Her expression became innocent.

It was a face that was oozing with ignorance, a look that anyone can recognized at a glance.

\textit{Confucius? Why'd he show up? Why is it sounds cool?}

\textit{What's the rest of it?}

"Okay. See? Is there a great senior here who can explain the story of Confucius and the Heavenly King to her, the youngest?"

For a moment, they seemed to be looking at each other, and then soon hands started to appear here and there.

"Yes. Young Master San was the fastest. Why don't you teach her a lesson?"

"Yes. When Confucius arrived in the state of Jin, a man named An, who admired the way of the scholar, presented him with a precious bead."

There's a reason why the saying goes, 'Beads become treasures only when they are strung'. In this day and age, beads must first be strung on a string to become decorations, no matter where they are hung.

So, when Confucius tried to thread the beads, he saw that some idiot had already drilled a hole in this precious bead, and the hole was so twisted and complicated that the thread would not pass through.

After a long struggle, Confucius finally threw down the beads and grumbled. Then, a thought suddenly occurred to him: wasn't stringing beads originally a job that women specialized in?

So, instead of struggling and wondering on your own, why don't you ask the woman? She'll tell you.

So, as a result, he succeeded in stringing the beads beautifully, and this was because he politely asked the answer to the question without looking down on her as a lowly woman.

Therefore, asking when you don't know is something a gentleman should do and is not something to be ashamed of.

Also, since each person has different strengths and knowledge, we should never ignored others and acknowledged that we all have different wisdom.

This was also what Tian Yuxue wanted to tell the scholars of the Hanlin Academy.

That was when.

Qing smiled bashfully and acted coy in a way that anyone who knows Qing would ask if there was something wrong with what she ate.

"Wow, you're so knowledgeable. As expected from someone who's educated, you explain things so easily. Thank you."

"Ahem, that's, that's too much praise. There's no one here who doesn't know that…"

"Yes, Heavenly Blossom Sword, despite being a martial artist, sought out this scholar, admiring his world-renowned scholarship. He came to me more than ten times a day for thirty days in a month to ask for my wisdom. Even when Liu Xuande sought Zhuge Liang's wisdom, he only sought him out three times. How much more so, when she knelt before me more than ten times a day, seeking the words of a sage! I was so impressed by her that I took her on as my disciple."

This story had already been agreed beforehand.

Still, you had to make sense.

\textit{I wondered who would believe that.}

"Ohhh."

\textit{Hmm. They believe that again.}

Qing, who had difficulty controlling her facial expressions, pretended to be shy and put the veil back on.

'Ah.'

The scholars released a sigh of slight regret.

So, a strange junior came to Great Study Hall and the lectures lasted for one day, then two days, then three days.

"Great Scholar. What do you think? Do you still think I should expel my disciple?"

"Oh, really. I'm so dumbfounded. They're so obsessed with their studies to impress a woman?"

The Great Scholar was convinced.

Tian Yuxue believed in Qing's beauty.

Taking off the veil and showing off her face, saying she likes smart people, and with just one word, even simple-minded people will be fired up to the max to give a lecture.

So, the person who solved her question tried to explain it as simply as possible, and the person who sent her a word tried to look cooler in some way.

The problem was that Yulin's method was to expand the scope of the interpretation with plausible explanation and adding it to the scriptures.

So, at every lecture, they came out sharpening their knives and a fierce debate unfolded.

So Tian Yuxue was satisfied.

The Great Scholar was also satisfied.

Bachelors who participated in high-level lectures would also be satisfied.

Only Qinq that's dissatisfied.

"I'm going to go crazy."

"Cheer up."

"You, traitor."

Chen Changming completely avoided her studies and went to work at the Hangsan Martial Hall.

The Hangsan Martial Hall was a branch of the Hangsan Sect, and the Hangsan Sect was a member of traditional Daoist sects, so it seems that there was no burden in visiting them.

When she returned home around dinnertime exhausted and watched Chen Changming fixing her wooden sword, she felt a surge of desire to go and swung a sword herself.

\textit{Why am I the only one studying when we came together?}

"What are you doing?"

"Preparing for the exam……"

Qing was not in a position to be looked down in front of the smart people of the Confucian scholars in exam.

But why even did what Tian Yuxue told her to do?

She was hoping he would help her out a little.

But Tian Yuxue was busy.

She wondered if he's even sleeping properly while he's interpreting the treasure map.

How on earth do you interpret treasure map?

A few wedges, a few squiggles,

And if you held an angle here and an angle there up to the light, a few more lines appeared, and if you put them in water, a few more numbers appeared.

When Qing saw it, she wondered what kind of map it was, but since Qing came, he's been cooped up all day looking at the map, except when they're eating together.

So, the teacher was so focused on the map that he's rarely seen.

Changming'er would go to the martial halls in Taiyuan and sparred with them for a while, then returned home.

Qing sighed deeply and looked back into the books.