\chapter{Journey to Taiyuan (3)}

"Huh? But why is someone from the Seol Clan doing the work of the Taechung Sangbang?"

"Ahem. Well, what else would you do with a smart fellow?"

"Even if that Seol fellow is a great intellect of the province, is it alright to use him like that?"

"Well, um, yes! It's all for his own good. The Seolga Sanghoe is just a small thing, not a vessel that can contain him. Yes. That's all it is. Not that I'm taking advantage of him or anything."

Still embraced, Qing cocked her head.

Is that so? Does that make sense?

"Hmm. That Seol fellow is quite a big figure, though."

"Yes. A big fish needs to go out to the sea."

One should also hear the perspective of the big fish, who was being pushed out of a freshwater pond into salty seawater just because he was deemed too big.

But before Qing could think more deeply, a luxurious table, just to Qing's liking, greeted her.

There were various kinds of meat, braised until tender, some sweet and salty, some spicy, and some left unseasoned to preserve their natural flavors.

"What's all this? I was planning to eat inside."

"It's just some leftovers I warmed up. If you don't eat it, I'll just throw it out to the beggars."

Qing has a universal palate, where all kinds of food are delicious, regardless of preference.

If there was a preference to speak of, it was for soft, tender meats.

And soft meat was originally made by braising over a long period.

As such, it was also a high-end dish that requires a lot of effort.

So Qing knew it was nonsense.

Leftovers?

What were they eating to have such precious braised meats left over in such variety and abundance?

But Qing didn't question it further.

She knew that they were probably feeling bad that she was returning to the Divine Maiden Sect without having eaten a proper meal with them.

So, what could she do?

She just had to pretend to be fooled.

As she sat down and picked up her chopsticks, a lady from the merchant association, whose face she didn't recognize, placed a thick banquet-style bowl for soup in front of Qing.

"Um… Miss, this is."

Somehow, there was a familiar, piquant, spicy scent that made Qing sniff unconsciously.

She stirred the contents with her chopsticks and was shocked.

"Huh? What? Wow, what. What is this?"

"A Heavenly Maiden tried to make it. Could you please try it and give us your esteemed opinion-?"

Before she could finish, Qing hastily took a spoonful and slurped it.

A spicy yet refreshing, rich yet cool broth went down her throat.

Qing's eyes immediately widened.

It was like the scent of home from an unfamiliar restaurant. No, this wasn't just a scent, but a soul, a spirit, an inherent national essence.

A broth made by simmering bones until they melted, with plenty of onions and cabbage to bring out the vegetable broth, but not too much water.

Garlic, onions, and scallions were added, along with a generous amount of chili peppers, despite their high cost. The broth was then filled with pork, various offals, and tender beef short ribs.

For vegetables, there was an abundance of cabbage and radish greens, making it a hearty, spicy meat stew that was unique to Zhongyuan.

It could be said to be a dish that perfectly captured the essence flowing in Qing's blood.

"No, wait, rice, rice, rice, is there any? Cold rice would be even better. Hurry, hurry!"

"Rice! They say to bring rice! Serve it chilled!"

Suddenly, the lady exuded an immense aura, but Qing was too focused on the soup to notice.

However, Yeom Huiyeong, sitting across the table, had an expression of utter disbelief.

Why is the Supreme Holy Maiden acting like a kitchen maid? She looks like a handmaiden, so she fits the role perfectly. She should just keep being a handmaiden.

As such, the chef's freshly cooked rice was purposely spread out and fanned to cool it down, a misdemeanor committed by fanning it with Inner Qi, creating a typhoon-like wind.

As soon as the rice arrived, Qing hastily dumped a bowl into the soup. Oh my god, it's Korean Beef and Rice Soup. How, here, wow, this, good!

"Mmm, this is it, this is it."

Qing emptied the large banquet-style bowl without even taking a breath.

Her body was so strong that she didn't even sweat, which was a great pity.

This kind of food was best enjoyed while sweating profusely.

"D-Did it suit your taste?"

"Yes, the best, it's the best. Wow, even in Zhongyuan, there was such a soup. What's its name? Where can I go to order this?"

"Ah……."

The lady staggered instead of answering, and Qing barely managed to catch her as she fell.

"Are you okay?"

"Y-Yes, I'm fine. It suited your taste, you say?"

"Of course. It's the best."

"What a relief……. I have no regrets now……."

And then, her head drooped.

Of course, the lady, the Supreme Holy Maiden of the Cult, had to be understood.

To these fanatics, obsessed with their faith, Qing was not human.

She was a divine being who had descended to the mortal world, and not just any divine being, but a merciful lord who was already answering their prayers in real-time.

Already, in cities from Gansu to Shaanxi and their surroundings, one could easily find unfamiliar statues.

They were statues of a female Buddha or Bodhisattva with a voluptuous figure.

Their distinctive features were the veiled face and the halo behind them, resembling a blazing sun.

This baseless Buddha, called the Holy Fire Buddha, was rapidly spreading with the claim that it protected the peace of the household and brought warm energy to one's future, thus bestowing good fortune.

In fact, there were already many testimonies of people who had experienced its effects.

Of course, most of these were spread by the cult's agents, and the rest were the result of the power of merchant associations that had taken over the cities, secretly pushing the agenda.

Thus, the cult's theologians were now openly setting up Holy Fire temples in the streets, preaching their doctrines under the bright sun, realizing the future that the Divine Cult had so long dreamed of.

So, for a maiden who had successfully made an offering to this divine being, she had accomplished everything.

A person can collapse from too much emotion.

Of course, this was all utter nonsense.

Qing urgently checked her pulse, but, hmm, she's perfectly healthy? What's going on? But what was the name of my soup in the end…….

Choi Leeong said it was a lady who had been watching over the chef when he was staying in Chang'an, and she had made the soup by analyzing Qing's meals.

He also added that her collapsing was something that happened occasionally, so there was no need to worry.

"Ah. So, I can't eat it anywhere else."

"If you miss it, just come back and eat."

It was a blunt statement, but it meant to come and visit often.

Qing, feeling a bit touched by the sentiment, made a playful remark.

"Gramps, what if I come every day and eat you out of house and home?"

"It wouldn't be a financial ruin if it's just because of you. And if it comes to that, then so be it. What else can we do?"

Then, after having some tea…

"I should get going now. I snuck out, actually. It's nice to be out of the house. The Zhongyuan is a much more livable place than I thought, but also even more of a mess. This is why seeing once is better than hearing a hundred times."

“Huh? Running away from home at that age?”

"It wasn't my fault. It wasn't my fault, since my aunt was the one who made it happen. Anyway, live long and stay healthy, Mother."

I thought Yeom Hui-yeong would stick around like a leech, but he surprisingly leaves calmly.

"Are you going to the Divine Maiden Sect?"

Nang Rang shook her head.

"Nang Rang is tired from the journey. I can't move any longer. This Nang Rang demands to be treated as a VIP by the Tianhua Merchant Association."

"It's not my merchant association. I'm telling you, it's not mine, okay?"

"If the Heavenly Flower Sword says so, then so be it. Anyway, this Nang Rang cannot move any longer. I shall faithfully fulfill my duties as a guest of the merchant association."

And Gyeon Pohui didn't visit the Divine Maiden Sect often.

Ximen Surin didn't particularly welcome her.

If she was just going to be there with her energy drained, making her shoulders droop, then Huimae might as well just stay at the merchant association.

Qing ascended towards the peak of Divine Maiden Peak, carrying a large bundle on her back, full of gifts for her fellow disciples, as was customary when returning from a long trip.

Of course, her body was so strong that it wasn't heavy at all, but her heart felt light and as if it could fly.

Perhaps it's because the road home feels more comforting and easier than home itself.

"Ah! My eyes suddenly went blind! There's a radiant light shining in the middle of the night!"

"Aigoo, this radiance must be from Senior Superintendent! Welcome back, Senior Superintendent! Wow, Senior Superintendent, it's been a while, but you look even more beautiful than I remember!"

"It's totally Mara! Maratang!"

"I love Maratang! It's like a whole new world!"

"I love Senior Superintendent too! It's totally Maratang!"

Two disciples, Yeonseo and Sarang, were chattering and making a fuss.

Qing chuckled and responded to their antics.

"Do you two always stand guard only when I arrive?"

"Hehe, we do. The Divine Maiden told us to greet the Senior Superintendent, so she set our duty schedule like this."

"But Maratang? Is Maratang on the menu?"

"Kyaaak, I love it so much! But only once a month……"

"I wish it was every day."

"No. Then, doing the dishes would be a huge chore. You haven't been on duty when Maratang is served, have you? That red oil is seriously the worst of the worst."

"I don't care! But behind you, gifts! It's gifts, right?!"

"Let's go inside first. I have to greet the Sect Leader and my Master first."

"Ah, yes! Then we'll come by later!"

"Ta-da! Grand Martial Aunt has returned! The most beautiful woman under the heavens is back!"

Seeing the two making a fuss, it seemed like life in the Divine Maiden Sect was still the same, with the addition of a new dinner menu being the only unusual thing.

"Elder, you're here? Ah, you've become even more beautiful."

"Oh, come on. Nothing's changed. Everything alright?"

"Everyone just gained a bit of weight from eating well all winter."

After the surprise visit from the Empress, the Divine Maiden Sect became the owner of all the nearby land.

Their already sufficient finances overflowed, so they decided to significantly enhance their meal plans.

The Divine Maiden Sect believed in doing things themselves, but during winter, there wasn't much to do besides gathering firewood.

So, with more delicious food and less activity, everyone had gained some weight.

"Ah, it's the Junior Grand Martial Elder! When did you arrive? Candy?"

"Candy."

"Candy!"

Qing handed out candy to the second-generation disciples, as if she had it stored away for them.

But? Why are there so few looking for candy?

Wasn't my return practically synonymous with candy?

How well were they eating that they didn't even look for candy?

Didn't we always used to be hungry for something sweet, you, me, and us, the Divine Maiden Sect?

Qing tilted her head and headed towards her own residence near the peak of Divine Maiden Peak.

She planned to quickly unpack, greet the Sect Leader, and then go see her Master.

As she ascended Divine Maiden Peak, the wind became quite strong. Yes, this wind. Feeling this makes me feel like I'm home.

Near the top of Divine Maiden Peak, facing the Yangtze River, Qing's residence was constantly blasted by strong, knife-like winds all year round.

Of course, the cold wasn't a problem for Qing, no matter where she was.

Oh, I forgot about it because it's been so long. It was just a simple observation, as she flapped her Daoist robe in the fierce wind and climbed the stairs three steps at a time.

Then, Qing's superhuman hearing picked up a different noise mixed in with the wind, a sharp sound cutting through the air, like whoosh, whoosh.

Qing turned the corner and saw a tiny hut.

In the front yard, a very small, not-yet-fully-grown child was swinging a sword.

It was the still-tiny Jin Jangmyeong.

Why is she swinging a sword here?

Since her work hours are over, she should have free time, but why here?

Could she be getting bullied?

But until last year, Jin Jangmyeong was the youngest of the main disciples and wielded considerable influence.

Because she was small enough to fit perfectly in one's arms, she was constantly held by the disciples.

But has her swordsmanship improved?

It was the Divine Maiden Sword Formula, a powerful sword technique consisting of crude strong strikes for a woman's swordsmanship.

The force contained in each movement, with Sword Qi faintly visible in yellow, was quite powerful.

More noticeable than that was the tangible aura emanating from Jin Jangmyeong's entire body.

It seemed as if her Inner Qi was stirring with her emotions, and it was because she was engrossed in training with all her might.

…no, that wasn't it.

It was just that she was sweating profusely on a dark, cold evening, and she was just emitting steam, more precisely, sweat vapor.

"Oh. Little one. First-Rate martial artist. Middle? Late?"

At this, Jin Jangmyeong spun around and widened her eyes.

And then, she immediately dashed forward, but stopped one step short of colliding.

"Huh. What's wrong?"

"Sweat. I sweated a lot."

"Who cares about that? Come here."

"It's damp."

"Do you want to ruin this reunion? Hurry."

Only then did Jin Jangmyeong release her sullen expression and jumped, clinging to Qing.

Qing hugged Jin Jangmyeong tightly and whispered in her ear.

"Hmm. But it is a bit damp. Quite a lot, actually. It'll drip if I squeeze too hard. It'll pour." 