\chapter{Journey to Taiyuan (6)}

If one had many teachers, one naturally had to act as a disciple to many as well.

Therefore, the disciple should certainly visit her second teacher and pay her respects.

Qing hadn't thought of him as a teacher initially, but thinking about it, wasn't it her first master who suggested she acknowledge the second teacher?

Still, now that she thought about it, she did miss that insidious smile of her second master.

And so, there was one person here who was extremely excited.

"What should I pack?"

"Clothes. Underwear. Towels. Needles. Thread. And a sword."

"Is that all? How much gold and silver should I bring? I have some pocket money saved up. Should I just bring it all?"

Is she a kid going on an overseas trip for the first time or something?

Qing chuckled at Jin Jangmyeong, who was unable to contain her excitement, and answered.

"Aherm, put that away. Why would you need gold and silver?"

"I don't need it?"

"I told you to bring a sword. Why would you need gold and silver when you have a sword?"

"……?"

"A sword."

"Is that right?"

Qing giggled and stroked Jin Jangmyeong's head.

Jangmyeongie is so short that her head is always at the perfect height to be stroked.

"Your Subordinate Uncle may look like this, but he's very rich, you know? You don't need pocket money to buy a toddler some candy."

"I'm not a child. I'm twenty this year."

"Twenty is totally a baby. A baby."

"It's only a one-year difference."

"Ahem. Can't you feel that one-year difference? Me, a Transcendent Realm Master, and you, um, let's not talk about it. One, two, three? They're all the same novices, so why even bother to distinguish them with numbers? I really don't get it."

"Hmph."

"Now. Go pack your things and get a good night's sleep."

"Okay."

She answered readily, but judging by her state, it was questionable whether she could sleep at all tonight.

And just as expected…

The next day, her eyes were swollen, and the whites of her eyes were bloodshot red.

She carried a bundle bigger than her own torso, but her movements were still light, probably because she was still a martial artist.

"Clothes. Underwear. Towels. Needles. Thread. What's all this? Are you opening a clothing store? Are you a peddler?"

"I only packed what you said was necessary."

"Aigoo. People will think you're making a perfectly fine servant girl do manual labor. Here, let me see. Hmm, why is there a blanket?"

The moment she opened it, a blanket popped out.

"Fourth Sister said I should be careful of the cold if I sleep outside."

"We're not sleeping outside, okay? And even if we did, we wouldn't sleep with a blanket. Hmm, what's this?"

"A windbreaker. Fifth Sister said I absolutely need it."

A windbreaker was a type of clothing, which in Qing's hometown would be called a cloak.

In fact, the only difference between the two was their name.

How could such a perfectly matching garment appear in different cultures?

Did people across the East and the West think it was cool to wrap themselves in a long piece of cloth, regardless of where they were?

Of course, that wasn't the case.

It was simply because the method of wrapping one's head with a long piece of cloth or leather and fastening it in front was so easy that even a monkey could do it.

It was just that in cold places, people used it to keep warm, and in hot places, they used it to block the heat.

"It can be useful, but you don't need it this time. Jangmyeong-ah, there's this amazing thing in Taiyuan called a house. It's an amazing invention that blocks the cold, heat, snow, rain, and wind. Ah, it might be hard to understand with just words."

"Hmph."

"Extra cotton clothes, you'll be too hot once we get there. Winter clothes, same reason. Why fabric? Repairs? Are you going to weave when we get there? A pot? A bowl? Why spoons? Ah, hemostatic medicine is well-packed. Hmm? What's this, jerky? Why is there so much jerky?"

"Fifth Sister told me to take it to eat on the way…"

"Excellent. Yes. This is what you should pack. Just like this."

"……?"

Anyway, Jin Jangmyeong's luggage became slim through extreme management.

After removing all the unnecessary household items that were almost at the level of a refugee's belongings, it finally looked like a proper Jianghu traveler's luggage.

Afterward, they greeted the Sect Leader, whose appearance was not at all familiar, and bowed to their master, saying they would be on their way.

Then, finally, they departed for Taiyuan.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Commonly, the groups of villains are called the Unorthodox Faction.

Here, the unorthodox referred to those of the heterodox sects and the demonic referred to those of the Demonic Cult.

But the villains of the world were not just those of the heterodox sects and the Demonic Cult.

So the rest were grouped together as those who deviated from the path, the heterodox.

In any case, those of the heterodox sects claimed they walked the heterodox path, and those of the Demonic Cult claimed they walked the demonic path, so the rest were called the pathless ones, the heterodox. This was the agreement reached by the righteous, heterodox, and demonic, without actual agreement.

Among this heterodox were the Blood Cult, human scum that needed to be eradicated.

And there were also those who always lurked in the shadows of Zhongyuan, such as the assassins, human traffickers, and butchers.

And then, there were the bandits.

Here's a surprising fact!

The Nokrim were not classified as part of the heterodox sects!

Even though the main business of those in heterodox sects wasn't much different from robbery, they at least didn't openly steal wealth.

The heterodox sects at least had some minimal justification, collecting protection fees without protection, revival funds without revival, and other taxes without rights through harsh means.

At least it meant they were acknowledged groups that the government turned a blind eye to, saying they couldn't intervene in martial affairs.

But what about the Nokrim?

Nokrim, for all its fancy name, were just bandits living in the mountains.

This could be seen from the fact that if a complaint was filed with the government to subdue the Nokrim, they would make excuses like ‘military matters are not under my jurisdiction', ‘the military is busy blocking the borders', ‘can't you use the police?', ‘then who will protect the city?'.

There was no need to even make the excuse of not intervening in martial affairs when it came to leaving bandits alone.

So when the third son of the Nokrim Chieftain came to visit, Sado Ryeonju's first thought was, ‘Why? Why would the son of a mountain bandit's leader suddenly come here?'

"Hah. You took down the Nokrim? A mere fledgling who has just reached the Transcendent Realm?"

"Didn't I say she used all sorts of underhanded tactics? Displaying his brutally murdered child, setting fire to the stronghold to disturb their composure, and then using poison, shouting ‘This is how your son was killed' while running away until the poison spread…"

"Would that even be real? Losers always make all sorts of excuses out of bitterness. Since they're also ashamed of themselves, they spout nonsense that even a dog wouldn't believe. If a Late-Stage Unrestrained Realm Master lost to a fledgling who just entered the Early-Stage Transcendent Realm, well, that's just being a asshole, isn't it?"

"So, what do you want to do?"

"Would swallowing the Nokrim help the alliance in any way? And he comes to me and says he'll give me the Nokrim if I avenge him. Does he think the Nokrim is something so valuable? If it were, I would have beaten up the Nokrim bastard myself long ago and taken all his children hostage."

Then, Sun Woong smiled.

It was a big mistake on Wang Dae-yang's part.

Sado Ryeonju didn't need the Nokrim.

Just like how the Blood Cult messed up things in Guangzhou, having the Nokrim involved would only make people say, ‘I knew it, those bandit bastards, they're finally showing their true colors,' and lower the entire standing of the Sado Alliance.

Sun Woong's admirable expression made Bu Anpyeong burst out in anger.

"No, who's the strategist here!? Are you a strategist just because you're sitting there, hindering me? I put you there to think for me, so why are you making me use my brain!? Do your job! Your job!"

"Since the alliance leader is already wise, there's no need for me to do anything. But there's no need to discard a card that's already in our hand. I'll just attach a Master and manipulate him. A mountain path that connects the entire Zhongyuan is still a valuable resource, isn't it?"

At that, Bu Anpyeong's grumbling subsided, and he continued.

"And that Tianhuajian bitch, we can't just leave her be. Find a way to get rid of her somehow, create a justification for me to get involved, set the stage."

"Why bother?"

"It's fine to leave a crazy bitch alone if she can't tell up from down. She'll die eventually. Drowning in her own resentment is a martial artist's end, as she'll find out later."

Bu Anpyeong's smile disappeared.

"But now it seems she's not a stupid bitch. She knows how to hunt those stronger than her. She's only a Transcendent Realm Master now, the youngest Transcendent Realm Master? What's next, the youngest Unrestrained Realm Master?"

A mere fledgling of a Transcendent Realm Master took out two Unrestrained Realm Masters and burned down the Nokrim?

When Bu Anpyeong was at the Transcendent Realm, he couldn't even imagine how to do such a thing. It was a skill close to divine.

And that's just a Transcendent Realm? Then what about later?

"We can't let a bitch like that become a Master. A peerless Master who goes around cutting down every evil person she sees? We need to cut the weed before it grows any bigger."

Bu Anpyeong's eyes gleamed.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Before Qing left for Guangzhou, she had sent a letter asking if she could visit in the summer, and upon her return, a reply was waiting, grumbling about how hard it was to see her disciple's face.

So, according to the original plan, they were supposed to take a carriage straight to Shanxi Province on an express journey.

But there was a kid who kept asking, ‘So where are we going? What's in the middle? Where else are we going? What else is there?' every quarter of an hour.

It would be a lie to say it wasn't annoying.

But she couldn't just tell the excited child, ‘Yeah, we're just going to sleep, eat, and lie around in the carriage for twelve hours a day until we reach Taiyuan.'

So, what could they do? They had to make it feel like a trip.

So, instead of the super-express high-class carriage of a merchant association, they leisurely rented a carriage, visited famous mountains in each city they stopped at, tried local specialties, and headed north, and north again.

After a month of leisurely enjoying the scenery and playing with Jin Jangmyeong, who was excited to be out in Jianghu for the first time, they left Sanmenxia and were on their way to Yuncheng.

In other words, the journey had now entered Shanxi Province.

As they watched the scenery outside the carriage change, Qing, who had been idly looking out, turned her head at the sound of something being sharpened.

"What are you doing?"

"This. Sharpening."

"Huh? You didn't throw that away?"

"Not throwing away. Just need to sharpen the end round."

Qing had given her a small seashell earring.

She thought that if the broken, sharp part was rounded off, it wouldn't look like a broken item from the start.

Jin Jangmyeong carefully held the broken piece close and gently rubbed it against a whetstone.

After carefully grinding it, she blew on it and examined it from various angles, but then, not satisfied with something, she buried her head again and continued to sharpen the shell.

That was when it happened.

Clunk! The carriage bounced significantly after hitting a rock.

"Ah."

Jin Jangmyeong looked down at her hand with a sad expression.

The half-shell earring was now a quarter-shell earring.

When it was still half, it at least retained a circular shape that made one think it might have been a half-shell, but now, looking at just one piece, it was just a shiny something with no discernible shape.

"Ugh……."

"Hey, don't be too upset. I'll buy you another one."

"Okay……."

She answered, but her drooping shoulders showed she was quite dejected.

Still, she must have learned that delicate work in a carriage could lead to sudden mishaps.

Everyone learns through experience, right?

And just like that, as soon as they entered Shanxi, they had a grand initiation ceremony, and after another ten days…

A city surrounded by massive walls finally came into view.

The capital of Shanxi Province, Taiyuan.