\chapter{Crossing Our Blooming Wall (9)}

A skinny guy and a fat guy? In some ways, they seem like a perfect match. Even if you average them out, they're still seriously overweight.

From the perspective of someone who has been crushed under the weight of Povidone's belly fat, wouldn't there need to be five more skinny people to reach the average weight?

Qing pretends not to know for a moment.

The fundamental goal of the magic explorers was to acquire the magic of absorption, so unlike their enemies, the Blood Cult, it was not a matter of immediate life or death.

The goal was to catch him and extract his divine powers, so even if he was caught, he might end up in an even dirtier situation, but he didn't rush in and threaten to kill him right away.

"I'll go. How can I get you to believe that it doesn't exist? Should I stake my reputation on the monk, on the teacher, and on my grandfather's reputation?"

"The Zhongyuan were the corrupted, evil spirits, certified by the Buddha, guaranteed hellfire. Women were filthy beings, and no matter what they say, they were true Buddhists who will not be deceived!"

The world of the five filthy evils was referred to in Buddhism as the world of the five filthy evils, also known as Yeto, and refers to the world we live in now.

The opposite was the Pure Land, a pure world, a higher world of reward that was roughly equivalent to heaven.

For reference, in Buddhism, women were considered unclean and dirty beings, so the Pure Land was said to be a pepper field with only men.

It's not that women can't go, but women were also born as men, and the Pure Land has many dimensions, so there were some places that were exceptions.

In any case, the limitation of Buddhism was that there was absolutely no reason to accumulate merit and be reincarnated in the Pure Land.

Why, the neighbors don't use suicide bombers to lure us into going to heaven, saying that seventy-two beautiful virgins were supposed to be our dedicated servants.

If you were born a man, you would believe that death was an unavoidable fate, and if you go crazy and meet virgins, it would be a huge gain, but if you were fooled and die a dog's death, it was not a loss. The outstanding intelligence of the believers next door was precisely this rationality.

Anyway, he was a monk who was not good at writing Buddhist scriptures.

Is this world a corrupt and evil world? Yes.

Are women dirty creatures? Yes.

Qing was speechless.

"No, if you don't believe me no matter what I say, what do you want me to do?"

"Come with me, Seongsan Arabdaltaek! You four-year-old bitch of Zhongyuan, now was the time to become a monk and enter nirvana, free of charge! Be reborn as a true nun at the headquarters, following the eightfold path of righteousness, righteousness, righteous conduct, and righteousness! Then, you will gain the most precious thing in the world, my trust!"

The absurd statement that if you become a nun, and even a senior nun at that, you will be recognized, then they will believe you.

"No, I'm a Taoist too. I'm not a thief, but I'm a Taoist in my own right. What kind of monkhood was this? And your sacred mountain isn't Arab or anything like that. You're leaving the perfectly good Sumeru Mountain, Ganginpajebong, behind and moving the sacred mountain on your own? Isn't this pure cult?"

The sacred mountain of Buddhism in the West was Ganginpaje Peak, located in a corner of the land of the West, at the foot of the mountain range called the Himalayas in the hometown of Qing.

It was a name derived from India, and Westerners also call it Kailash.

"Wow. You know Ganginpajebong? You've earned a little trust from this Zhongyuan woman. She's already interested in Buddhism, and this was a once-in-a-lifetime opportunity to become a monk for free!"

It means that he just yelled at me because he thought I didn't know.

Of course, the judgment that he didn't know based on his ignorance was not wrong.

But ignorance no longer exists in front of the honey chestnut that contains the secret of nuclear fission.

"I am a true master, a woman of Zhongyuan, and victory was impossible! I will fly obediently into the Buddha's embrace!"

"There were times when the scale was short and times when the distance was long. Do you think you can win just because you have a high level?"

The village head of Cheokdan. A story about Qu Yuan. The poem "Qing" was written in Chinese characters, and it was a scene that would have made Cheon Confucius nod in delight.

but.

"Chuck? Village? What a strange thing! Speak in the Jungwon language, Jungwon girl."

"What? Why were you so angry? Do I have to listen to that guy telling me to speak in Zhongyuan dialect?"

"That's right. A great opportunity for you, woman. The Buddha has opened his arms wide. A once-in-a-lifetime opportunity to offer your divine power to the Buddha!"

"What about the divine power? In the end, those kids who only care about the magical power always say things like the divine power, the absorbing magical power, and-"

Suddenly, Qing bends his knees and lies down.

Above it, the giant body of King Fat Povidon, precariously cutting through the air.

As soon as he lay down, Qing suddenly stood up and stretched out his arm to grab his swollen ankle, and with a shout of excitement, his muscles bulged!

This would be roughly 400 pounds?

How can a person weigh four hundred pounds?

Qing'er Povidone, the ignorant lump of stone, spun around, and it hit the walls from side to side, causing them to fall down!

The human body moves forward, drawing a whirlwind of destruction, its speed was fierce and its destructive power was incomparable, it was truly a whirlwind of rotation, Ximen Qing!

Even if you exert a thousand pounds of force, the difference in mass between the two bodies was so great that you can't help but stagger and sway.

Even so, I managed to advance quickly, knock knock knock, and the human hammer, Povidone Hammer, came out, and in the middle of the night, the wall was suddenly demolished and came crashing down!

"Eww! Eww, stop, stop! Eww."

Povidone Place The blood rushes to the head and it feels like I'm going to die.

In fact, there was absolutely no reason for a drone of this caliber to get caught and spin around.

Because if you bend down and fight back, those who wield the human toilet, or rather the human weapon itself, were either second-rate or first-rate who have been beaten and weakened.

But what about povidone?

The thickest part of the body was the waist, so I wiggle my spine with all my might.

It was a shame that we need to investigate the truth of the rumor that he was not able to clean up after himself.

"Oh, don't come!"

The frightened Amukhaprap takes a step back.

But the blue actually increases the speed.

It was easier to control your body because it rotates vigorously two times per breath, because the higher the rotation speed, the more stable the center axis becomes.

However, since it puts that much load on the axis, it stimulates the muscles of the auditory nerves in real time and makes them grow.

"You crazy thing! A giant pig with nothing but scaffolding! A shit pig! A roasted, edible beast that doesn't help a single bit! Even Buddha would slaughter Povidone! \#\#\#! \#\#\#\#\#! \#\# \#\# \#\#\#\# \#\#\#\#\#\#! \#\#\# \#\# \#\#\#\# \#\# \#\#\#\#\# \#\#\#\#\#\#\#!"

Amukhaprap retreats, hurling swear words at Povidone.

The automatic translation of the blue makes one wonder if Povidone's parents were truly human, and judging by the child's appearance, it was likely the result of loving animals, if not loving them, and he conveys the well-being of his parents who were burning in hell for their sins.

If he had heard of povidone, he would have made a statement that would have made him decide his life or death immediately, but he didn't know what the chief said anyway, and even if he did, he wouldn't have time to listen to anything when the blood rushes to his brain and the pressure in his brain skyrockets due to the violent rotation.

Kookbang!

A huge disaster bursts out from the alleyway, with the walls on both sides bursting apart!

Gyaaak! Eww! Run away! At the sound of the civilians' screams, Qingdo couldn't help but frown.

And with the mighty bang of the Heavenly Demon Lord's Rimbo, he engraved his footprints on the ground, adding the recoil to his rotation speed and letting go.

Povidone, who surpassed Zhongyuan and broke the world's fastest speed, flew like a cannonball and crashed into the wall of the poor Sihewon's luxurious manor, entangled with Amukhaprap!

Two people exiting through a thick wall.

Qing'er Beetle, oh my, did you go too far?

Nighttime pedestrians staring at the bloodied woman with astonished eyes. And the martial artists people in between.

"Thousand Flower Sword! It's the great absorption method!"

"God! God was over there!"

They were annoying little kids who won't listen no matter how many times you tell them there's nothing.

In the first place, when a person was immersed in one thing, normal thinking was impossible, and faith reaches the realm of belief, so even in the homeland of the world Qing, which was much more developed than this, there were idiots who insist that the Earth was flat. Even if they were abandoned in space, they would die thinking, "Oh, it's round, so it must be flat."

So, what would it be like in the uncivilized Zhongyuan?

And all the guys waiting for Qing in Hangzhou were just those kinds of guys.

"Really, I'm going crazy!"

It would be better to have a three-headed man and a five-headed woman, but isn't that at least considering them as people?

What the hell was going on there, these kids were really just watching.

The new Qing form splits into eight parts and spreads in all directions.

Neungpa Mibo was a method of stepping on a target by drawing a straight line with it and standing two chapters behind it with your back to the target that twists and digs into the energy of the world.

What if there was a person between the targets and the distance between them was more than three chapters?

A translucent blue new form leaped over the nameless tourists and slid into view right before the man who was still screaming, "Sucking magic! Sucking magic!"

The blue hand pierced the man's stomach and slapped him.

"Here's the new one- kekekeke!"

"You fight with your mouth? Even this little brat claims to be a warrior and walks around with a sword."

Qing did not hide his contempt.

If you want the divine power, you should either rush in like a man or just shout from afar to gather people. It's obvious why.

Since I don't have the skills, I'm going to gather some people first and watch from afar while waiting for an opportunity.

Qing roughly pulls out what's in his stomach and with his other hand pulls out the sword from Muin's waist.

It's heavy and bulky, so it's hard to say it's a good sword, but it's a heavy and sturdy sword, so I like it much more than Mahi's fluttering sword.

"Okay! The human god was coming out! If you have any complaints, come on! Let's do it with life or death like a warrior!"

Qing shouts confidently and then immediately deploys light attack and runs.

The goal was another float.

The troll, seeing the blue approaching with a menacing demeanor, runs away with a tired expression.

"Huh? What was it? Why, why were you doing this!?"

"The divine power you have been searching for, now the divine power will come to you!"

"There's a misunderstanding, it's not me, I'm not interested in magic at all!"

"You're hilarious! You don't know I was talking about the Absorption Method here? If a guy opens his mouth, he should be held accountable!"

"No, I just! Just! So-"

"Shut up! You're going to gather people together and exploit an opening? Do your own work! Figure it out! If you don't have the skills, give up, or dare to ask someone else for help? You despicable little bastard!"

"No, that's what you should be saying now-"

"No questions asked!"

"You're talking nonsense, but you're just asking questions?"

"That kid! He talks so much!"

Qing's lightness was already highly praised by those in authority and was the best in the world.

The insignificant running of the trembling, screaming in fear of the blue, could never shake it off, so a single slash of blood, a single line of sword energy, split the space and blood spurted out.

"Ugh, uh, save me……"

"Remember this. The scars on your back were a disgrace to the martial artists. Know shame."

Qing was looking down at the fallen tavern with cold eyes.

Then, squeak squeak, the sound of the flute makes the head turn and the eyes turn fierce like axe blades. Who was it, what kind of bastard dares to make that sound?

But that too for a moment.

Between alleyways, jumping over walls, climbing the eaves of tall buildings, jumping off the roofs of houses.

One by one, armed unarmed men continued to appear on the road and off the road. Some were in their pajamas after waking up, some were holding spears upside down as if they had come out in a hurry, and even some were carrying bottles of alcohol in their hands.

Qing's expression suddenly distorts.

No, what on earth was the magic that was causing this chaos in the middle of the night with so many people?