\chapter{Crossing Our Blooming Wall (8)}

The representative of the Blood Ramun clan closes his eyes tightly and lets out a deep sigh.

Something even more horrific than the worst-case scenario I had ever feared had happened. That bastard Mahi would rather die peacefully than that bastard Shiksimmagun run wild.

Damn it, it's so unfair that he left first, leaving only a message telling us to hurry up, and then ended up in such a miserable state, and now we have to bear the consequences.

The only way to survive was to catch your enemy, wrap him up nicely, and offer him up.

"I just heard a report from the lady in the text that the Lord's daughter was on the verge of death after being brutally tortured by the Cheonhwa Sword. Now, the Cheonhwa Sword and the Blood Ra Sect were sworn enemies. Could you please consider our plight?"

"Ahem."

Chaeun-sok pretends to cough, moving his lips. This was the appearance seen when sending a message.

"Once the investigation was over, I'll subdue the Heavenly Blossom Sword and send it to you. So, why don't you step aside for now? I'll make sure to explain my Blood Clan's concession to the Lord, okay?"

The Blood Moon leader's intention was strong, so if he were to subdue the Cheonhwa Sword and send it to me, he would just send it back to me, telling me to kill it.

Of course, I have no intention of simply joining the Sa-pa-ryeon just because I am Qing.

The scheme of these two conmen who deceive and deceive each other was truly sinister.

Then, this time, the famous beasts of the Blood Moon rush in front of Chaeunsok and kneel down.

And then, wouldn't it be to bow down and beg?

To Qing, it seems like the bitches who used to run around on all fours with their necks tied up were now bowing their heads and doing the same things they always did.

"Elder, please reconsider our grudge just once. Yes? Please…!"

"I beg you! To have to turn back with your enemy before your eyes? What could be more miserable and tragic in this world?"

"Please, I beg you, sir!"

"Ahem, hey, don't do that."

Chae-un-sok can't hide his embarrassed expression and was trying hard to give these guys hints to do something.

But inside, I'm starting to get a little angry.

No, I made a concession to take care of it later so that we could both resolve it amicably, but what kind of farce was this that was making people feel uncomfortable?

If you reject me here and take the Cheonhwa Sword, what will happen to Yeon's reputation?

Anyway, these Blood Ramun bastards were also greedy for magic, so they're just thinking about stealing the Cheonhwa Sword while making all sorts of excuses, and these bastards…

However, Qing slowly put his weight on his front paws.

For Qing, kneeling was just a step backwards for momentum and a blueprint for the bigger picture.

Just seeing him kneeling and bowing deeply makes me suspect that he might be preparing to ignite the propulsion system.

And, as expected.

The beasts fly all at once.

A fierce rush worthy of the authorities on imitating beasts that fly and crawl on all fours!

"Huh!?"

Chaeunsok's reaction was a step late.

As if they had been bitten by the dragon, they hung on tightly, biting the dragon's limbs, and the beasts all they could do was to back away hesitantly.

Although he was a master, he didn't fall down.

But that too for a moment.

The beast that was being dragged around with its back bitten desperately reached out and soon found itself between his legs.

And then I clench my fist-

"Ahhhhhh!!"

A spine-chilling, heartbreaking scream!

Just as a woman's breasts were not protected by a self-defense weapon, neither were a man's two beads.

There was no master or subordinate in the pain of the palace, and the inside of the body was completely destroyed.

He urgently tramples the ground.

"Elder!"

The blue one rushed in with a sharp scream, its desperate tone representing its desperate state of mind.

Anyone can see that they were rushing to save the elderly, but what was their true intention?

No! I can't give up the final blow!

The blue leg hit the side of one of the beasts!

The sensation of a rib being broken, a painful scream of pain, and a sac that hangs down.

Qing grabs her hair and throws her away, then hurriedly squeezes herself between the women.

They were a bunch of beasts that have been crushed and banded together.

He didn't notice Qing right away, so Qing pushed through the crowd, the smell of blood wafting in, Qing stretched out his hand, tracing his face, beard, neck, further up his shoulder, and finally past his collarbone-

Qing's fingers dig into Chaeun's chest.

A hand full of strength forcibly spread my ribs apart, and my fingers dug deep into my chest, clutching my heart tightly.

The world's greatest evil force that crushes and crushes the heart muscle.

"Ugh."

Chae Woon-sok, aged sixty-three. Born a man, died a eunuch.

It was a vain end for a master who was evaluated to have reached the realm of Hwagyeong and become a great pillar of Sadoyeon.

He died while being trampled by countless women, so you could say he was a good man.

"What the…!" "Master!" "Master!!"

"Hit! We must seize the Heavenly Flower Sword to survive!"

"They're attacking! Everyone, draw your swords!"

Then, the Blood Moon warriors revealed their true colors, their swords flashing, their sword energy and sword power intertwining and clashing in countless trajectories, and sparks flying.

As the filling sagged, the beasts that had been chewing on flesh, drinking blood, and scratching at hides stopped.

They slowly raised their upper bodies and exchanged satisfied glances at each other.

The beastmen suddenly feel a sense of unease.

What the heck, it seems like there's a spy among us?

Of course, when everyone was covered in blood and ugliness, wouldn't one person be strangely beautiful and shine?

"Oh. Did you get caught?"

"You, Cheonhwa-"

The jaw of the beast that was talking suddenly turns around.

The eyes of the beast that was hit with a straight jaw open and its pupils roll up.

Then, Qing's hands stretched out left and right, grabbing at a strand of hair. Then, with incredible force, he brought his fists together, and the two heads attached to them were knocked out from the center!

"Gyaaak!"

Two heads hit, one scream.

Well, if the head was cracked and the brain and brain fragments spill out, even a wild beast, let alone a wild beast, wouldn't be able to make a sound.

"Kyaoo!"

"Say it out loud!"

Qing shouted, raised two fingers, and thrust them forward, shooting them into the holes parallel to the middle of Qiao's face.

Kyaaak!! Kyaoo, who covered his eyes with a sharp scream,

Huh, if the scream was supposed to sound like a human, what the heck was that beast sound?

Are these monsters made by feeding them beast hearts instead of human hearts?

If Siksimmagun had heard that a cow walks the moon and steps on a mouse, he would have been so shocked that he would have shouted at him, asking how he knew.

Unfortunately, there was no Shikshimmagun in this place and Qingdo does not know anything.

"Khuuuung!"

"you also!"

The blue bird flies up, shouting loudly.

The knees that had been raised flexibly to the level of the forehead lowered the bridge of Kkuheung's nose.

Then came the cold, angry cries of the blue dragon that had climbed onto his chest, alternating with the flashing of both fists, and the eerie cracking sound.

"I! -Pak!- Person! -Pak!- With words! -Thud!- Do it! -Chop!- I said! -Thud!-"

Qing throws down the blood-curdled Kuheung and glares at him with a fierce gaze that was filled with all sorts of ominous colors.

"Do you guys have anything to say? Kyao-oh, keuh-heung, what's next, au-u? Umm-eh? Ko-gi-oh?"

"Eek!" "Hiccup!" "No!" "No!" "I'll tell you something!"

"Tch. They say you have to beat up animals or people to make them listen. Give me the leash!"

"yes?"

"Give me the leash! Don't you know what a leash is? Can't you untie it? Should I take off your balls and then untie you?"

"Okay, wait a minute, this was coming loose, coming loose."

"Hey, over here!"

"Tsk. Anyway. You guys think you're lucky."

Qing growls, takes the leash, puts it around my neck, and kicks the ground.

She landed on all fours in the middle of the fight between Hyeolramun and Sadoyeon, then quickly twisted and escaped, looking like a beast herself.

The remaining beasts of burden fell. More than half of them made a splashing sound.

The blue dragon swiftly crossed the battlefield in the shape of a zigzag. Anyone who saw it was a long-haired creature running on all fours with a leash, and it was clearly a wild beast.

Thanks to this, the Sado-ryeon warriors flinched and dodged, and the Blood Moon warriors shouted and pointed their fingers at the enemy, but neither type blocked their path.

So the blue flies across the battlefield to the onlookers in Hangzhou.

As the onlookers hastily pushed and pushed to make way, Qing jumped on all fours!

"Ugh!"

Qing also made a beastly sound once.

It would have been like a tiger leaping over human barriers and running wild through the streets of Hangzhou at night.

It was a blue that leaped up the wall of the pavilion, ran across the eaves, touched the roof, and ran to the neighboring street, then reached a house, snatched a piece of clothing from the clothesline, and quietly landed in a back alley.

"Oh my gosh. I thought my heart was going to burst."

Running on all fours, it was inevitable that it would sway uncontrollably. The punctured area sent out a brutal commotion, sending out excruciating pain that made people scream, "I'm dying, I'm dying."

Qing put her hand on his chest and felt around.

"It's really torn, s …

The sound of the wind blowing through the teeth was loud as the blue that touched the affected area hardens.

This was definitely going to leave a scar.

If I get some Jechangsan from Lan-ah and apply it, I can erase it in a month or two, but, um, I don't want to get caught.

Qing first wraps his upper body tightly with the clothes he stole, then unties the leash around his neck and throws it away.

That was when.

"A deceptive ghost, but he himself was incapable."

"Huh?"

"Because I have mastered the wisdom of all things. The shallowness of Zhongyuan woman was a trick. You exist within the palm of the Buddha's hand."

An unusually gaunt figure appears across the alley.

Qing recognized the person.

\textit{A strange monk, uh, what was the strange monk's name?}

"Yumomahop\footnote{魚墨麻合; hemp-wrapped fishcake}?"

"I am Amukhaprap! You rude Zhongyuan bitch! Even Buddha will not forgive you for playing around in the human name!"

"Hmm. I think Buddha will forgive me."

"I have been greatly insulted, you wicked Zhongyuan bitch! Hand you over to me! Then the Absorbing Law will be safe."

\textit{It seems like he's saying that if I hand over the Essence Absorption technique, he'll pretend not to see it.}

Qing roughly understood.

"I told you there was no such thing as a Essence Absorption technique. Why can't you trust people? How can I give something that doesn't exist? Should I make it up and give it to you?"

"The mouths of those Zhongyuan bastards were a cesspool spewing lies. Absolutely filthy! Even Buddha acknowledges them and condemns them to hell."

"No, who taught you Zhongyuan language? Was it the Buddha himself? No, if you're going to learn, learn from the Zhongyuan's Buddha."

"It matches the head of a stupid bitch dog. Buddha Zhongyuan it's replica. All Buddhas produced in India."

\textit{Umm, come to think of it, that's true.}

It seems that he was a monk who was good at Buddhist scriptures.

But why was that guy so rude?

"Anyway, I can't claim something exists when it doesn't exist. This was so frustrating."

"I agree. Those wicked people of Zhongyuan will be punished if they lie. If they just surrender their power, there won't be any bloodshed."

"Really, I'm going crazy…"

Qing pretended to wipe her face with both hands and glanced behind her.

Well, was this the only guy?

But with just a quick glance, the giant figure filling the alley immediately caught her eyes.

This was Povidon, the giant fat man who, despite his huge body, stealthily and quietly closes the distance without making a sound.

Povidone, that fat guy was so tough.

And did you two eat together?

While the slim guy was drawing attention, the fat guy pounces on him?

They didn't seem to get along, but was it like childish guys become friends while fighting or something?