\chapter{Crossing Our Blooming Wall (1)}

Qing enters the guest house, pushing through the curtains made of wooden beads strung on ropes.

In the middle of the night, the first floor of the inn would usually be quiet, with one or two waiters dozing off at the table.

This was Hangzhou, still bustling with people sharing drinks, a scene that seems to have lost track of time.

The thick grains of the curtain that had been pushed through were colliding with each other before the sound of them cracking had even stopped.

"Welcome."

A graceful waitress, as if she had been watching the door the whole time, rushes in and greets me.

"Food? Drinks? Room? Bath?"

"Uh, let me have some drinks first."

The Qing Dynasty's military forces were shaking.

Then the waitress's eyes narrowed and she asked again.

"Really? That wouldn't do, would it? Drinking while someone's waiting upstairs. was that okay?"

The spirit of Qing flashed through him.

This girl, she's not a slut, she's a bitch named Nyeonyeong.

"Old floor, West Room. Stop doing anything else and get out now."

"Wait, you knew I was coming?"

"I didn't know? I just threw it because a tall, three-headed woman was holding it. Otherwise, I would've just been treated like a crazy woman."

Oops. Qing realized his mistake.

Then the woman looked at Qing with a smile.

It was such a hateful expression, I clenched my fists tightly. What on earth did this expression mean?

Does that mean you want to get hit?

That was when.

"Here, Jeomsoi!"

"Yay!! Sir! I'm going now!!"

Suddenly, the woman shouts a loud answer, as if from the roar of a lion, and runs towards the table where Jeomsoi was looking for.

Ah. I guess the point was right.

What was it? were you a part-timer and a salesperson?

Qing scratched the back of his neck.

Miss, I was planning on sneaking in just in case and then surprising you while you were sleeping.

If you don't have the internal energy, you can just turn your head and pull it out while they're sleeping without any defense, and it won't be a problem whether you're a master or a servant.

For reference, in Wulin, the act of turning the head and pulling it out was not usually called a joint technique.

Qing'er looked at the woman who had turned into a sincere and earnest person, and then giggled.

Man Seo Moon-Qing, you can't leave feeling defeated, even if you leave having won.

Apparently, Nyeonyeong said, "Jungs with free will?" She said they weren't her subordinates and she didn't give them orders. She just let them live however they wanted.

I don't know what his ulterior motives are, but I'm sure he didn't lie.

"Here's the guest! Oh! Hyang! Jang! Yuk! And Gam! Ho! So! Heung! Ju! Du!!! Bottle!!!"

I thought she was undercover, but she was surprisingly a very skilled fortune teller.

The voice was also loud.

Qing's eyes were glaring evilly.

Is this what you mean by serious?

So, instead of going up the stairs, Qing sits down at an empty table and starts talking nonsense.

After that, the woman who was busy running around finds Qing sitting at the table with her hands slumped over, not seeing her master who had asked her to meet him.

Then a woman comes running, lighting a twin flame.

"Hey, what were you doing? Get up there right now-"

"Oh my gosh!! I thought I was going to lose my neck waiting!!!"

Qing interrupts with a shout.

"you?"

"Is this place discriminating against people?! Oh my! Even after waiting for thousands of years! Why doesn't Jeomsoi even give me a glance? Do you ignore people just because you look a little sad? I was going to wear all of this today! All of this! Everything! Everything!"

Qing lifted the sack and slammed it onto the table.

Then, all the yellow gold coins pile up like a stone tower.

Anyway, Qing was a real rich guy.

People's eyes were focused on him.

The shabby appearance of the blue, contrasted with the glittering pile of gold.

"You, you, what……!"

"Look, people! I stumbled and fell into the mud, and my body was cold and shivering, so I tried to soothe my stomach with some precious wine and soak myself in hot water to avoid the aftermath, but, oh no! Well! That bitch named Jeomso only looked at me and didn't answer when I called her! She can ignore people, but this was so shameless! No, even if a dog had been there, she wouldn't have ignored me like this!"

Then people started talking.

"Huh, huh?"

And since he made such a fuss, other people couldn't help but rush in.

If he were a bastard, he could have mobilized gangsters to ask where they dared to act, but it would be difficult for a wealthy person who could build a fortune with gold on the table to become a bastard no matter what he did.

A dotty, her hair disheveled, as if she had just woken up, jumped out like a master of lightness and then, with a thud, threw herself down on her knees in front of the blue.

"Oh my gosh!! Customer!! I'm sorry!!"

"What? You? were you in charge here?"

"Oh my! Oh my! Oh my! That's right! I'm the very merit of Manwoljang! This child has only been working for so long! I don't even know you! Oh my! What were you doing, you punk! Why can't you get down on your knees and apologize right now!?"

"Oh, that's not it."

"What do you mean, no! Didn't I clearly tell you the way of Jeomsoi? When you enter a guesthouse, you were all guests, so treat them with respect like an elder! Why can't you apologize quickly? Didn't I say that Jeomsoi's knees should be stiff?"

"No, that's it."

"hurry!"

The senior sergeant spits fire.

It was no exaggeration to say that Hangzhou Jeilgaekjan's branch was at the pinnacle of branch stores.

Even if it was just a small matter, wouldn't this be the appearance of a great master? Wouldn't his fiery roar have been imbued with a stern authority, like a tiger roaring or a dragon striking down lightning?

The woman starts to cry, then kneels down, bows her head, and apologizes.

"Ugh, wrong, wrong,"

"Huh. Really? Did I really do something wrong?"

"This is, uh, sorry, sir, ugh……"

It seems like he was quite resentful and angry, and his voice was trembling and choking up.

A triumphant smile spread across Qing's face.

This was something that was nothing special and was rushing in.

"Huh. Okay. I'll just let today pass, seeing your good looks. Listen, where's the best room at the Hangzhou Jeil Guesthouse I've only heard of? Since I'm in Hangzhou, I should at least try to stay there at least once."

Qing, who had easily subdued the nameless zombie, climbed the stairs in triumph.

However, as you go up, your feet become slower and slower.

Seriously, it's tiring and annoying to have to go around asking people to impersonate you.

Because she seems like a really bad and useless bitch.

No, people can sometimes commit fraud in their lives.

Did I commit fraud by impersonating someone or did I do something dirty or bizarre to ruin my reputation?

Of course, of course I did everything.

But if you're a member of the blood sect anyway, what difference does it make if you hold a grudge?

Isn't it just the same as adding alcohol to alcohol or adding water to water?

Rather, it increases notoriety.

Since the Blood Cult's notoriety was growing, shouldn't we be receiving thanks instead?

Then the old floor.

Come to think of it, was it really right for luxury rooms to be on the ninth floor in an ancient, primitive Zhongyuan city without elevators?

Now was not the time to be thinking about other things.

The room that Qing was guided to was the Jar Room, the only top-class room left on the old floor.

As it was the best hotel in Hangzhou, it was only natural that the top-class rooms were also extremely luxurious.

But Qing didn't pay any attention to him and went straight to the outside wall door and jumped onto the roof tiles.

I walked down the hallway and checked the location of the study room, so I moved silently and jumped as if I was flying over the narrow eaves of the ninth floor.

The outer door of the study room opens silently.

And the body of Qing quietly enters without a sound.

A ghostly infiltration worthy of a divine weapon!

"Oh my. were you coming in that direction?"

As soon as I heard it, I was startled by the welcoming voice.

Qing's eyes meet Yun Yuanying's, who was lying on a wide bed covered with a thin silk quilt and only turns her head.

Qing awkwardly raised her hand.

"Hmm. How were you, Nyenyeong? Weren't you sleeping?"

"Hmm. That's a difficult question. If you were to call sleep the act of closing your eyes, letting go of your mind, and quietly feeling only the passage of time? Yes. I was asleep."

And then a welcoming smile appears on Bashishi's face.

A sickly beauty with a pale complexion and thin lines who looks as if she might suffocate at any moment, with a pitiful smile as if she were forcibly burning her own life out.

Qing stares blankly at the sight for a moment.

No, you need to come to your senses.

That face was really crazy.

"Haha. I never imagined you'd mobilize the military? That's too much."

"Huh. I didn't break my promise. Okay? I'm going now."

"Oh my, isn't it time yet? You should apologize to me, right? After thinking about it, I think you caused a scene at the black spot and mentioned my name."

"Oh. Right."

Oh, right? It's the sound of a bursting suit, enough to make a normal person's blood pressure soar and their tendons and veins bulge.

Yun Yuanying just lay there and smiled.

"Okay, sorry. Okay? I'm going."

"Really, Miss Ximen. It's incredible that such an insincere apology exists. But."

Unyeonyoung's smile becomes deeper.

"Is it okay for you to be so stiff?"

The shape of a sword rising above the bed.

But Qing snorts, "Huh?"

"It doesn't work anymore? Why, even if I cut your throat?"

"Oh my. How could I do that? Oh, what a shame. How cute you are, trembling and watching me closely. But even now, I like the way you take advantage of my kindness and act confidently."

And then, only then, did Yun Yuanying quietly raise her upper body and get out of bed.

The thin blanket covering her falls away, revealing her bare white body without a single thread.

I couldn't help but drool at the sight of Qing.

Oh. What a windfall. No, no.

"Are you trying to seduce me or something? Would that even be seductive? Gulp, gulp."

"Hehehe, I'm glad you seem quite satisfied."

"What about satisfaction? Why were you stripping naked and sleeping? I'm not some worldly slut. Sigh, no, why do I keep drooling?"

It wasn't something that Qing should say.

There were some people who sleep naked, but there was only one shameless person in the world who sleeps naked with his friends.

"Oh my. It's surprisingly comfortable in such a luxurious bed. It's not embarrassing to be single, anyway. If you try it yourself, Lady Ximen, you'll understand. How can I describe the feel of silk brushing against your skin? Swish, swish."

"Certainly, that's true."

"……?"

Unyeonyoung tilted her head.

Then, perhaps thinking it was just the usual nonsense, he clapped his hands together to lighten the mood.

"Aren't there some differences between an apology and a contrived apology? An apology was sufficient if it's sincere, but an apology requires proper compensation."

"Isn't coming all this way supposed to be compensation? After making you suffer like this, what do you want in return?"

We need to hear more in detail about what 'that hardship' is.

At this point, Yun Yuanying seems like a bodhisattva.

Of course, where in the world would you find a Bodhisattva who breaks the record for the greatest evil deed in the history of observation every time you see him?

"It's not a difficult request, was it? Just, help me with a bath. Lady Ximen was looking a bit out of sorts, too. This was a good opportunity."

"Huh."

Then, Yun Yuanying smiled.

"Let's wash together."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Madam Mayi."

"You want to fall behind…? Get out…."

Mahi was getting irritated.

Well, forcing yourself to wake up was a fairly unpleasant experience.

However, what makes Mahi different from others was that her growls were sincere and without any falsehood.

however.

"The Thousand Flower Sword has appeared."

"Your Majesty!"

Mahi's eyes lit up!

The Heavenly Sword has appeared, so why were you looking for the Lord?

It was because of Mahi's love that she defeated the Cheonhwa Sword - the Jeongsa War broke out - the Lord asked about the reward - the Lord asked her to marry him - Gyaaak!

Mahi, who had been rolling around on the bed from side to side, with a pale face and a commotion, saying, "What should I do, what should I do?", finally came to her senses after a long time.

"Ha, creeping out like a rat in the middle of the night, you're just like that hypocrite of the political faction."

What's the point of trying to weigh it now?

But that behavior was already familiar to the disciple, Yeonyun.

Pretending not to see anything, he asks calmly.

"What should we do?"

Mahi chuckled at that.

The sharp fangs sparkled in the light of the lantern.

"What should I do? Let all the kids go, and then contact Unnie. I'll go myself, so hold on tight."
