\chapter{Crossing Our Blooming Wall (7)}

The women sit quietly, their heads pressed against the floor.

Aren't you ashamed of making a "Kyao-oh" sound with your own mouth? Even if it's a throat-scratching sound like "Gurur," "Ah-hung," "Au-unni," "Au, goosebumps. were you in your right mind?

Well, if you were in your right mind, you wouldn't be running around on all fours with a leash on.

It's a blue that even has the luxury of thinking about other things.

It's not that it's not, it's secretly comfortable.

The pressure of just fifteen women cannot invade the body (unofficial) of the strongest in Zhongyuan.

Even if the beasts scratch with their hands, they were actually unable to do anything because they were blocked by the Cheonjamsa's clothes and were just pulling and stretching them.

So, I'm going to pretend to be subdued and take a deep breath and observe the situation.

Qing pretends to be subdued and listens.

-Did you get hurt?

-What kind of dog was this? Hey, stop talking nonsense and bring me a net, no, a steel wire. What kind of power do you have? It's not like you're a bull.

-Hehe, isn't that right, cow?

"Are you kidding me? How many people were dead? Ha, tie them up properly for now. The Lord will personally interrogate them. What the hell, can't you all just get out of here? What the hell were you seeing!? It's a Blood Clan event, just ignore it and go to sleep!"

Would a Zhongyuan person miss watching the fight?

An angry voice that chases away onlookers while making a fuss.

But what about the Blood Moon?

I feel like I've heard it somewhere?

I had probably glanced over the names of the big sects thanks to Ximen Surin's common sense, so from what I've heard, it must be a pretty big sect.

Well, the Blood Cult guys wouldn't dare call themselves the King of the Blood Cult or openly operate as the Blood Cult Food Clan.

If you think about it, it was a perfect disguise.

If you just look at what the Sapa and Blood Cults do, there's no way to tell them apart, right?

Since it's just a bunch of evil and misdeeds anyway, the difference was whether it's very harmful or just harmful.

If you think about it, there must be so many blood cultists mixed in among the Sapa. After all, the Sapa people aren't of any use to the world. They need to be wiped out completely.

That was when.

-Wait! Stop!

"Who were you? Reveal your identity! Those who dare to interfere with the Blood Clan's events will pay the price!"

-Ahem, that young punk was really a brat. I am an elder of the Sadogunahhapjongyeonhapyeonhaphoe and a member of the Justice Execution and Law Enforcement Council.

-Yangyangcheolsangpwon!

I've felt this way for a long time, but I think the Sado-ryeon guys were always very stubborn about making up words to make themselves look good.

The long name of the Apostolic Union was like that, and if you look at the way the Apostolic Ten Great Natures use only the title names, isn't it just like a dream?

And what about the board of directors? Why was it a footnote?

Of course, I still understand.

Because originally, only worthless people risk their lives for their titles.

-Ahem, I apologize for my rudeness. But this woman, no, this man, was a sinner who murdered the disciple of the text without any reason, and the Blood Clan wants to pay the price.

"The Cheonhwa Sword possesses the most ruthless magic. I feel sorry for you, but for the greater good, wouldn't you yield to me first? I promise to send you to my Blood Clan once the interrogation of the criminals was complete."

-That requires the Lord's approval. We were simply following orders.

"Oh, you bastard. We're not all part of the same family. What would the Blood Lord say if he, the Sadogeon, briefly handed over a sinner to us, who were like family to him?"

It's really unfortunate that they didn't even know that they were blood relatives and just fell down like that.

It looks like even the Apostolic Union was looking for magic.

The Blood Cultists won't follow suit, so they'll just bicker for a while.

Qing quickly opens the martial arts list.

Shouldn't we figure out what the true energy was that has been pushed in and taken hold of without permission?

The Seopsimgong has ten stars, and a red border. They say he's the ten greatest demon lords in the world, but he's only red. And how did he get in there and take over without permission?

But if you think about it, it doesn't seem like it's really a loss.

Anyway, I wouldn't have learned it with my own money, or rather, with my own training center, so I'll just consider it a bonus.

Before Qing clears the martial arts window, he raises the levels from the Joyful Yoyo Gong to the Twelve Great Stars all at once.

Hey, next time you're really going to die.

Then, the two things that I'm concerned about with temporary registration were the pair of martial arts of Talmyeongjeongsim and Talmyeongdo.

Each one was gold and red. I can't do the brainwashing right now, so I'll leave them aside for now, but I can't tell if this was magic or not.

"Talmyeongdo, a sword that takes away life. Just hearing the name alone makes it sound like a demonic art. But what about Talmyeongjeongsim? A righteous mind that takes life? Hmm, if I ask Master.

Oh right. There's also Zhuge.

Miss, I should have asked you sooner. I didn't ask even one thing like this and just played around.

Qing blames her laziness and then turns her attention to the outside world.

-Are you truly intending to defy the will of the Apostolic Alliance? No matter how much power you've recently expanded, do you really think you'd abandon our Apostolic Alliance?

-Even if you say so, I have no authority. I only pursue the sinners of the sect.

-Is this really going to happen? How dare a small sect dare to go against the great Apostolic Alliance?

Before I knew it, I was full of people who treated me poorly.

Qing's eyes sparkled. If we leave it like this, won't the Blood Cult and the Sapa fight each other?

But the anticipation was short-lived.

-Ahem. Then, I guess our Dharma Assembly's Xueryeoldae will also have to accompany the Heavenly Blossom Sword. I need to speak directly with my sect leader. If I'm being completely blocked, huh? Tsk.

Those hot-headed bastards, if words don't work out, you should just pull out your swords. What kind of conclusion was that? Just call them hot guys, call them hot guys. These guys only act tough when they see a weaker guy than them.

"Sleep tight!!"

The voice of Qing was clear and beautiful, even when surrounded by a crowd of women.

And the women's hill trembled, then, with a bang, the blue body rose and the women with leashes were thrown in all directions.

At that impressive appearance, the Blood Cult members, the Sapa warriors, the warriors watching, and the onlookers in Hangju were all shocked and their eyes widened.

"Wait a minute! Everyone! Don't be fooled. These guys aren't the Blood Cult, they're the evil offspring of the Blood Cult, the Shiksimdan under the command of the Shiksim Demon Army!"

Their surprised expressions became even more surprised, some even hitting their foreheads as if they were going to fall over, while others grabbed their heads with both hands and raised their elbows. It was truly an unimaginable sight!

"What, what!? was there any evidence, any evidence?"

"These beastly women were proof of that! They're the Blood Demons, monsters of the Blood Cult, monsters that covet human hearts! Aren't they clearly abnormal?!"

Then, people's expressions were not very good.

The leader of the elite combat unit, the Sado-ryeon Jibap-gak, simply called Jibap-gak for short, lets out a cough.

"There seems to be a misunderstanding. Even though the Blood Clan was reprehensible, their beastmen aren't sorcerers, but rather warriors who have mastered a form of authority."

"Huh? A beast of burden?"

The beast was a beast and the lady was a lady, so if we break it down, they were beast ladies.

Qing frowns at the strange name, but Chaeun-sok adds that he was a member of the Sadoryeon and protects the Blood Ramun.

"It has already been verified by the Sadolyeon, so you should not dare to mention the Blood Cult."

"But, no matter how you look at it, this isn't normal. What kind of woman in the world would put a leash around your neck, make animalistic noises, and run at you with her teeth?"

Qing tries to protest, but for some reason, no one seems convinced.

Why on earth? was that normal? My stomach was so stuffy I was about to hit my chest, but the punctured wound kept hurting, so I held it in. And then—

"I hear you're going too far. Even if you're called the Heavenly Sword, the most beautiful woman in the world, don't you think that's too much?"

"I only learned the art of the Earth Beast, but I have to be treated like a monster. This was just too much!"

Sharp, crying voices.

When Qing looked back, he saw the women who had shaken themselves off and stood up on their feet, glaring at him.

"No, it could stand on two feet. No, it could talk?"

The blue was absurd.

Then what about the beast's howl? He was imitating the beast in his right mind?

At the same time, oh my.

Come to think of it, even if it was a blood cult, would they have blatantly exposed the blood demons in broad daylight, or rather, on a night as bustling as day, in front of the people?

Those four-legged beasts must have had a way of avoiding suspicion even when they were being watched by others, so they must have done it with great confidence.

"But……! These kids, Blood Cult, ugh."

Qing was wronged. Very wronged.

Just as the enemies were always astonished by Qing's strong words, Qing was also so shocked and speechless that he couldn't say anything.

No, they're real blood cult kids!

Those kids were blood cult kids, why don't you believe me? Why do they give me that look while clicking their tongues and shaking their heads?

The fist of the blue was trembling.

It's not an atmosphere where you can believe it even if you try to force it now.

Since it's something we can deal with later, let's just get out of here first, let's get out of here first, no, really, you Blood Cult kids, I guess I'll just leave you alone, no, phew, calm down, calm down.

No, but it's a blood cult, right? Why don't you kids with eyes know it's a blood cult even when you see it? You should just pluck out all their eyes!

Qing'er sighs deeply and calms herself down.

Huh. Do you think I'll lose just because of that?

"Ahem. Anyway. Everyone, I've already revealed that the Absorbing Magic was part of the Blood Cult's evil plot."

"Because there's no evidence other than your testimony, Heavenly Blossom Sword, the Sadoyeon simply concluded that he couldn't be trusted. If you feel wronged, why don't you go to the Sadoyeon together and sincerely explain yourself?"

It was a sophistry that made the tendons on the foreheads of the magic explorers who heard it stand out.

What qualifications does the Apostle have to call you? In the end, isn't it just a request to hand it over because the Demon Lord wants it?

They say they'll give you a dog after you've finished cooking, but for someone who ran all the way to Hangzhou to wait for Qing, isn't he just a pickpocket who's relying on his weight class to get in the way?

Qing answers him.

"I understand. Since the girl was a member of the Jeongdo Wulin Alliance, some may not believe me, thinking that even if the Alliance proves my innocence, it would ultimately be protecting my family. However, if the great swordsmen of Sado Geon-ah judge whether or not I am a demon, wouldn't the people of the world be convinced?"

This means that he will accept the investigation of the Apostolic Union.

The person who was most surprised by this was Chae Woon-sok, who had brought up the subject.

He must have been so surprised that he asked back.

"Huh? What? were you serious?"

"Of course. The great swordsmen of Sadogun-ah simply wish to investigate, and since I do not possess any magical powers, was there any reason for them to refuse?"

"Oh, yeah. That's right. That's right."

Chaeun-suk has a sour expression on his face. He soon nods and agrees.

"Wait! Thousand Flower Sword! Where were you going!"

Then the Blood Moon warrior shouted.

Qing doesn't stop, just turns his head and responds calmly.

Still, wouldn't it be much better to be on the side of the Apostolic Alliance rather than the Blood Cult?

At least the Apostleship pretends to hide its true colors and hide its body in public places, so there was no immediate danger.

"I'm going to be questioned by the Apostles. Do you have anything to say?"

"That, that won't do, that won't do!"

"why?"

The blood cultists were confused.

Isn't this wrong? Should I just leave the Heavenly Blossom Sword alone? But how can I do that in this situation?

"What, what were you talking about? Blood debt! We need to collect blood debt! Do you dare to touch the Blood Gate and escape?"

"You drew your sword first and attacked me, so I was only protecting myself. Why do you call this a bloodbath?"

"Hey, don't be ridiculous! You were the one who first attacked me by framing me as a member of the Blood Cult—"

"Ah. I guess the Apostolic Society members can investigate and decide on that too. Right, sir?"

Qing looks at the filled stomach and smiles.

The law enforcement officer was momentarily taken aback, but soon comes to his senses and says what he needs to say.

"Well, yes, that's right. Well, I'm not unaware of the Blood Clan's position, but I will conduct a thorough investigation to ensure the truth was clearly revealed—"

"Oh no, oh no! Miss, Miss……!"

A shout that rudely interrupts the words of an elder from the Great Apostolic Church of Korea.

The blood cultist who went into the guesthouse to check on the girl ran over with a pale face and whispered.

The complexion of the Blood Cultist who came forward as a representative also became so pale that one could hear the sound of blood draining from his face.

Well, you must have seen that girl trembling like a worm while being well-dressed.

Leave me alone? Throw away your enemies? Judging by the way Mahi and all, that father must be no ordinary father.

If you leave me like this, will my father understand and say, "Oh, I see."

Qing raises one corner of her mouth.

So, what do we do now?
