\chapter{Crossing Our Blooming Wall (15)}

Tang Lan-ah was desperately trying to treat Qing's wound while he sits cross-legged.

"I, I can't live, I can't live……"

The hand that had been pouring hemostatic acid and applying a thick layer of ointment, running up my thigh, stopped at my chest. No, why was this kid again, really, really… … .

The child's vision becomes blurred by moisture.

Even if you knew that it was a miracle that it wasn't torn in half diagonally, and that its muscles were as hard as iron that even needles couldn't penetrate, wouldn't it be a miracle that its stomach didn't split open and its internal organs didn't leak out?

The little girl shivered and said, "This, this, why, why aren't they taking off?" and took off the vest and pants she was wearing and wrapped them up.

I applied the blood-stopping medicine and the gold-smelling medicine from Dangga, the best pharmacy in Zhongyuan, but the muscles were so hard that they can't be sewn up, and it's clear that it will break the concentration of the Qing, so the timing was not right.

So there was nothing left to do.

But, but… … !

Still, I can't help but fidget and can't leave her presence, worried that my head might droop even now, or that I might just sit there like a tall Buddha statue, wondering why this tall girl was acting like this, what should I do, what should I do…

That was when.

Suddenly, one side of my vision brightened, and I saw a flower blooming softly behind Qing's head.

"ah."

The little girl looks at the flower from afar.

Qing'er was this desperate, so I can't just tremble like this.

And then he wiped his tears away with his sleeve, and after his wrist passed, his remaining eyes remained firm and unshaken.

The little girl picks up the medicine bottles and other items that have fallen on the ground and stuffs them into her sleeves, into her chest, and into her skirt.

The Sword of the Great Emperor of Zhongyuan.

It was the sword of the Supreme Emperor that can cut down ten thousand enemies with one swing.

Just as Qing was startled and asked what kind of nonsense such a thing was at the martial arts festival, even back then it was just black energy, the sight of Kang-gi growing continuously was an absurd miracle that leaves the onlooker speechless.

So, it was Gong Sun-Yaoyi who blocked the rear defenses alone.

"It's long! It's long!" "Get out of the way!" "It's just stretching!"

They were bloodthirsty demons who act like idiots, but aren't they extremely clever?

They were constantly changing their attack routes, targeting the young lady of the West Gate, and realized that if they attacked all at once, they would be annihilated.

They opened up distance and ran at each of them, trying to take their breath away. They jumped up and down, crawled, and varied heights, even jumping diagonally and holding out the corpses of their dead comrades to block their momentum.

Even so, Gong Sun-Yaoyi held his ground and did not let a single one pass, as his experience in swinging a sword from the earliest memory of his past was as adept as his ability to deal with them.

But how can a human being wield the authority of a new being?

So, it was a river that flows, burning life and its source.

My life, which I should have willingly sacrificed for my family, how could I be ashamed of sacrificing it for a friend who was as precious as my family?

For my only friend, no, not my only one anymore, but my most precious friend.

But, it's a shame.

If I could live even just one day longer, even half a day longer, even just an hour longer, I could spend that much more time with Lady Ximen.

But even though it's regrettable, it's not a waste.

What good was it to use what you need when you need it?

Xue-i-ri and the blood demon had many things in common.

"It's cold!" "It's cold!" "Ice Dragon!" "It's cool!"

First of all, the vocabulary level was the same.

I would say no, but wouldn't anyone say that I use the same level of vocabulary?

And secondly, don't spare your body.

Only attack, ignoring defense.

Of course, Xue-i-ri may feel wronged.

For the Blood Demons, command was a paramount priority, even more so than their own well-being. They've been modified to be so determined that they'll risk their lives to carry out orders, regardless of whether they're injured or killed.

Compared to that, what kind of martial art was Binggong?

The destructive power and lethality were the worst, but the aftereffects were so bad that it's fortunate that the frozen, burst, and broken wounds only leave scars.

Because it was a martial art with a messy and dirty aftereffect that will not be erased for a lifetime.

So, if an ordinary martial artist were to meet a master of ice magic, he would be afraid and lose his momentum, but this was a martial art that was performed with the strong will to kill me and make you a cripple.

Even so, Xue-i-ri was still able to drive away countless ice dragons with great momentum. The first reason was that her originally poor internal energy was supplemented by the acquisition of the Ice White Divine Skill and the subsequent poisonous energy.

But the reason Xue-i-ri fights was not just to repay that favor.

The only kindness shown to me in Xue-i-ri's life was a small act of sympathy from my uncle, Xue Ga-nom.

A warmth that I couldn't understand because I'd never had a family.

But now I understand.

The warmth of a mother holding her child, the secret affection of an older sister caring for her younger sibling, and the feelings of that older sister when she looks at her younger sibling.

Xue-i-ri, who had lived alone and isolated, now has a family. Even though they were strangers, not even of the same blood or ethnicity.

The warmth that my people and my blood relatives have never given me.

So, Xue-i-ri breathes out cold air again.

My mother, my older sister, but since I'm older, my younger sister.

"Sister Tang! This way!"

The Ice White Dragon strikes the enemy.

One blood demon falls down, but another blood demon jumps over it and runs towards it.

Xue-i-ri raised her left arm to block the attack, and pulled her right arm tightly, ready to give up one arm and take her by the throat.

In an instant, a thick, sharp needle appeared in the eye of the blood demon that was floating in the air and rushing forward.

"Hey! You! were you really going to act like a crazy bitch? Don't you want to take care of yourself? Do I have to take care of this too!?"

"Yeah. I don't like it. No."

"What? Why were you talking like that, and why were you speaking informally!?"

"My heart."

"What, what! You! You! You act so cautious and unapologetic in front of Qing'er…!"

"Sister Xue! Jump!"

Xue-i-ri jumps high, scattering frost in the air.

Then, a corpse of a blood demon brushed past my feet, collided with the blood demon that was rushing towards me, and rolled on the floor.

The second reason why Xue-i-ri was still so energetic.

Because Zhuge Lixian matched it well.

Looking at the situation, Murong Zhuxi's care for Xue Iri was a huge loss in terms of military power, so he took on the role of coordinating and taking charge of the formation instead.

Of course, since it was a very wild and violent snowstorm, it was possible for it to penetrate places beyond my reach, but at the time, I was able to avoid major crises by asking for help from Tang Lan-ah.

"Sister Xue, come here! You can't deviate! If you miss even one, it'll reach you!"

It was Xue-i-ri who returns to her seat in a hurry.

Suddenly, the thought occurred to me that I don't understand why Ximen Soju was just called Noona, and the others were called Noona Xue, Noona Dang, and Noona Moyong, but I immediately reach out my arm again to the blood demon that was rushing at me.

The two swords of Nan-gong Shencai, the swords of Changsanya that flash in the sky, come together in one place, drawing the most perfect path.

Emperor's Sword, Nan-gong Shencai grits his teeth.

Isn't this a crude sword that was shameful to the name of an emperor? How can a weakling who was only good at blocking and avoiding call himself an emperor?

So there were three swords!

It was that moment. Following the trajectory of the sword drawn by Changsanya's sword, an invisible aura fiercely tore through space.

Nan-gong Shencai collapses awkwardly and barely escapes the destruction.

The thoughts of a warrior who has reached the state of Hwagyeong.

An invisible blade that was released half a beat later than the sword's trajectory. If you hadn't recognized the swordsmanship earlier, it would have been a terrible dark sight that you would have been unaware of.

Wind Dragon Ascension Sword. When reaching its peak, the blade of wind follows the sword and bites the enemy.

The record gives a very accurate description.

Changsanya swung her sword from afar toward the crouching Nan-gong Shencai. The sword swept horizontally across his lower body, followed by Pungah.

But, Kang!

Peng Daesan, who flew into the air, blocked the sword strike with his sword.

The crescent moon that Changsanya was drawing below suddenly breaks off in the middle.

The sound of the sharp wind barely brushed Nan-gong Shencai's neck, leaving a small thread.

"Huh, thanks!"

"hurry!"

The mountain of Pangdae rolls on the ground and roars.

It's a call to get up quickly and help when it's time to be thankful.

Nan-gong Shencai, knowing him, jumped up, and ran with both swords down, their tips brushing the ground. Ding! He cut off Changsanya's sword as it tried to cut through the air again, and pushed it back.

Truly vile and dirty swordsmanship.

I just want to spread the distance and cut down the invisible, dark sky from afar.

Originally, such means usually involved the consumption of a huge amount of money, but would a Blood Sect demon who had grown his dantian with a human heart have ordinary internal energy?

Rather than counterattacking, he chases after you and tries to cut off the roots of your swordsmanship, so even if you try to deflect it, the recoil will cause you to open up space.

It was an endless game of tag, and it was an unfair situation where the tagger got hit and rolled around unilaterally.

Changsanya draws her sword.

Anyone can wield a sword swinging in the air, but Pang Dae-san still takes three steps and Nan-gong Shin-jae loses his balance.

No! Nan-gong Shencai forced his feet onto the ground, and with a thud, a sharp pain struck his knee. But Changsanya's sword was released and he swung—

Wedge! Clang.

A sudden shower of rain causes Changsanya's sword to fly upwards, out of its path.

The trajectory was just strange, and the energy contained within was so low that even if you just hit it, it will either scar you or ambush you.

But who would dare to block the secret power of the Tang family with their body?

My breath was foul, my body wants to breathe, my lungs can't handle it, my inhalation and exhalation collide, and my airway feels like it's going to burst.

Look at the shape of Peng Au.

He was covered in blood from the blow he couldn't stop, and he thought he would probably end up in the same state.

Peng Daesan strikes the ground and raises its body.

The pain from the deep cut on my arm was unspeakable, but I gritted my teeth and moved forward again.

Didn't you just brag and say you'd hold on and pretend to be cool?

After putting on a show of frivolous style that would make a great man like Jo Hyung, he couldn't just fall down dead in an ugly way and greet Qing with a gloomy expression after losing someone.

He's a selfish guy who, despite being his friend, interferes and helps without any reason, but he avoids and takes care of his own problems, so he doesn't even give anyone a chance to help him.

That guy has finally taken a step forward and opened his heart.

If you disappoint me now, you'll probably end up living your whole life like a fool.

Okay, then what can't be endured?

Just holding on, damn it.

Peng Daesan was gritting his teeth.

Barely holding on? Even though we're both at the peak of our power.

After defeating the enemy, he couldn't help but laugh at the sight of him looking bloody and miserable, saying, "Why were you so late? It's over, what more can I wait for?"

If I had known this would happen, I would have practiced.

I should have swung my sword once more while I was away on a trip to avoid nagging from my family.

When my older sister teased me, I should have avoided her and run away, but instead we should have shared the path and sparred again.

The time I've wasted so far was painful.

If I could go back in time, I would spend every moment practicing.

Yeah, except when I go to the opening ceremony.

Paengdaesan chuckled, and suddenly, without realizing it, a smile burst out.

Asura. A descendant of Asura.

And then I got hit once, and I thought, yeah, that hand really was sharp, and that was indeed fitting for a descendant of Asura.

At that moment, my eyes really lit up. Ha. Right. It was a fist as powerful as a wall.

In an instant, the strength contained in the sword stretches out like a mountain. And then, the left hand was pulled tightly.

A flash of lightning flashed from the side of the body.

Tick, the force released by Yedo collides with Changsanya's sword and he was pushed back without being able to stop it.

But in that very moment, in that very brief moment of collision and slowing down, through that very small gap, Peng Daesan's left hand extends out like a ray of lightning.

The power of the wall of chaos, eight seconds. As decided.

When you hear the sound and turn your head, lightning has already struck, because the force of the wall has already reached you and then it starts to shine and spit out its anger.

Changsanya sees the water running down her thigh and quickly pulls her foot away.

Peng Daesan's hand simply brushed past the enemy's spot and struck the air, but-

Kkwarung!

"Ugh!"

With the force of the wall, Changsanya screams and quickly retreats five steps.

In other words, only five steps away.

"How dare you……!"

Changsanya's eyes, having been hit once, rolled back again. It was as if the man in his mouth had a lot of patience.

So he holds the sword with both hands, and raises it high above his head and behind his back, his folded elbows looking up at the sky.

"no!"

The boy screamed and desperately reached into his sleeve, but all he could find was an empty inner pocket. Why of all things-

Wedge!!

Changsanya cuts through the air with all her might.

He simply swings his sword with all his might, his back bending, his knees dropping, and the blade sinking deep into the ground, all the way to the hilt.

It might be considered quite a savage sight for an martial artists vehicle, but half a beat too late, the power within it overpowered the form of the dark mirror, rushing towards it and right in front of my nose-

DENGGGGG.

The sound of the temple bell covered the world.
