\chapter{Crossing Our Blooming Wall (14)}

Blood runs thick on the ground, and a dreary red fog swirls through the air like a swarm of maggots.

On one side, a wall of writhing flesh reaches into the sky, stretching out countless languid tentacles and swaying without wind.

In the middle of it, a small hole appears through which people pass, illuminating the acrid floating matter of the rotten palace beyond the wall.

The gateway to the horse race!

Any human being would instinctively realize that it was a very dangerous place.

In fact, even instinct was not necessary.

Just seeing with my own eyes the disgusting sight of flesh floating on blood-covered armor and bones sticking out like reefs, blocking the sky, I knew this wasn't the right place, that this must be hell.

Yet, countless martial artists beings step through the fleshy orifices and throw themselves into the cesspool, and that number of demonic beings were born.

Even though I know it was ominous and harmful, I still cannot overcome my yearning for a higher realm.

Even the gates of the devil's mouth were open to free entry and exit at any time once you entered, so even if you resisted them once and won twice, they were still a temptation that lingered before your eyes.

Always there when you reach out.

Do you want power? If you want it, take it. It's reserved for you, and you can take it at any time.

So many drones fall down.

The realization of harmony was difficult and distant.

Since the path of the wise was difficult to see in life anyway, I would rather die than reach the next level even if it means going to hell.

And now, another person's imaginary world, a shadow appears in front of the gate of the devil's gate.

A visitor who rises and takes shape under the blood.

The image of an extremely beautiful woman.

The blood on the ground vibrated on its own, surging and splashing, and countless tentacles hanging from the flesh wall blocking the sky greeted and shook wildly.

Do you need strength? Come, come to me!

Even the most ferocious of evil spirits reveals itself, opening thousands of eyelids and drawing tens of thousands of eyes.

Countless people have passed through the gates of the martial arts, but from the beginning of martial arts until now, no one has been courted with such a warm welcome.

So the woman opens her eyes and looks at Mar.

Then he put both hands forward, clenching his fists so that the backs of his hands were visible, but only one of his middle fingers was straightened.

"What the hell were you talking about! Go eat some shit! You friendless bastard!"

And then, in a flash, it scatters into blood and disappears in an instant.

The gateway to sudden criticism or ridicule reveals its bewilderment with a quiet silence.

What was it? What was it?

[…]

The eyes of the evil star in the sky shake.

If that evil spirit, which we cannot tell whether it was a real evil spirit or a product of our imagination, a heavenly spirit or a blue spirit, could think, it would have thought like this.

Why on earth do you eat taffy? Why do you insist on eating taffy?

And why do I feel so dirty?

Qing opens her eyes and looks at the pure white snowy field.

Behind me, the long footsteps I have walked continue beyond the horizon drawn by the snowy field.

In front, an ice wall rises to the end of the sky.

It was an endlessly high cliff that seemed to extend to the end of the sky as far as the eye could see, perhaps even to the empty darkness beyond.

But even with the statue split by the thick ice wall, the endless unexplored plains that stretch out behind it hold a certain thrill that stirs the heart.

That was why I long for that realm beyond even more.

But the ice wall still refuses to listen.

I could tell at first sight that you lack the strength to dare to break through.

Qing realizes anew why the martial artists people were obsessed with horses.

The flesh wall opens its own hole when it sees someone touching it, a strong temptation that clings and tangles like a lewd prostitute.

But look at this ice wall.

You're just not ready yet, you're not good enough yet, so go back and work hard.

This was a very plain statement of fact.

It was a huge, indifferent pressure, as if looking at something worthless, without any emotion.

Yeah. It can't be broken or pierced.

That's right. It's impossible for me right now.

Qing admitted it.

But some certainty whispered in my heart.

I can do it. The path I've walked was the right one, the right path, and the path I'm taking was the right one. Soaring hope.

So the blue one runs.

The refreshing feeling of snowflakes touching my skin, the beautiful smiling face, it's so cheerful like a child running around.

So the blue one jumps up.

An unbreakable wall, it was like that from the beginning.

How can I break through this on such a high-octane subject?

Thin, white fingers were stuck in the transparent ice wall.

The hanging blue folds her arms and pulls her torso up, then stretches out her other arm and inserts the world's most beautiful, delicate fingers again.

Just because there's an unbreakable wall blocking your path doesn't mean you can't get past it.

If you can't break through, why not just get over it?

Footsteps that have passed, an old sword broken in half, and a long way to go before it can break down the wall.

I'm still lacking, I'm still lacking, but I'm trying to solve it on my own, this loser.

That's me.

Suddenly, a flower blooms on the ice wall.

The shape of a flower that reflects people, a flower that was ugly and pathetic, with petals carved out of a rusty sword that has been torn in half.

Inhwa, human flower.

Soon to be the center of the world.

Yeah, I did. So, did you add anything?

However, that does not mean that we can wait endlessly for enlightenment to come someday.

You can't just catch a suitable opponent and kill them one by one in a life-or-death fight.

So, Qing climbs the ice wall.

Oh, it's fucking cold, of course it was because it's ice.

Even though I hadn't climbed very far, the cold air from the ice wall felt like a knife cutting my hand.

No, not just the hands.

The ice melts on my body and I get soaked in cold water, and my wet body sticks to me, and the chilling cold seeps into my flesh, my muscles, and my bones.

Opposites attract.

The coldest yin energy resembles the hottest yang energy, so the pain it transmits also resembles it.

The cold that cuts through the whole body punishes the insolent human who dares to climb with a scorching heat like fire.

Qing grits his teeth.

Did you know that I would lose?

Suddenly, Qing looks up and sees the endless disconnection of the world.

Hmm. I guess it might work.

If you just put it in your mouth, no, no.

I went there, did a cool sign for mountain, spit out a curse word, and came back here.

If I go back now, does that make sense?

It's much better to bite your tongue and commit suicide than to die from being sold out.

So, Qing climbs the ice wall.

Go up.

And it's going up again.

Before I knew it, my whole body was covered in ice crystals.

The fingernails were broken and the skin was torn, leaving a bloody and cruel mark on the ice wall.

How long has it been?

One day? Ten days? One month? One year? Ten years?

Still, I couldn't get used to the cold, so every moment was a burning pain.

Even with the strength of a world-class warrior, after climbing the ice wall endlessly for tens, hundreds of years, my arms were shaking, my muscles were tearing, and it hurts like I'm being stabbed point by point. It really hurts. I feel like I'm going to die.

But still, Qing climbs the wall.

Memories that come to mind because they were hard and difficult.

My precious people.

If someone speaks first, they will definitely talk, so let's do it in the order we met fairly.

San-i, Zhuge-i, Geom-u, Nan-a, Ye, Mo-yong So-jeo, Gunyeong-i, they'll all be desperately buying time.

And we all have to go back alive together.

Master, I guess I'll have to take a picture of the mirror to avoid getting hit?

Jang Myung: Um, I'm sorry for ignoring you, but Jang Myung was really easygoing, really, really.

Master, if we take Hwagyeong, aren't we on the same level now? Heemae, Heemae's heart was completely dead. I'm going to throw away the rice cake dough. I miss Grandpa, and my advisor. I'll have to come to a conclusion with the highest intelligence in the province, the Empress Majesty, and our Lady Divine Maiden Sect, the Chirp Chirp chicks, the Xuega Store people, the Wulin Alliance, that bastard Changbin, who's a member, where was he doing what? Ah, I miss Hyang. was Jun doing well too? Was his name Bongchun or Chunbong, Naram's Georan Festival, Baekhap's daring exposure of her white chest, countless connections. And although I don't particularly want to see him, my son Hosoin, well…

As seen in the image of the Moon Sword.

It wasn't because I was good that I was the Heavenly Blossom Sword, the disciple of my master, the outsider of the Divine Maiden Sect, the divine dragon of the Wulin Alliance, and the president of the Half-Sword Ssangdohoe.

Of course, it was a well-known fact that I am good at something.

Since you guys admit it, I am the Heavenly Sword.

Without you, I'm nothing.

Another flower blooms on the ice wall.

The images of acquaintances smiling and making eye contact with each and every petal, made of fateful petals, were played on a moving screen.

Jihwa, flower of the earth.

The earth was the foundation on which people stand with their two feet.

The blue just rises.

Now, below, the ground was no longer visible, and above, there was still an endless wall.

Qing was not a human, but rather a block of ice, and he doesn't even have the strength to remove the thick ice.

It hurts, it hurts, it's hard, I can't breathe, my arms feel like they're going to fall off, my frozen flesh feels like it's being pricked with billions of needles and pounded with hammers, I can't even scream.

But I can't stop.

You must not stop.

Because my friends were waiting.

As the president, don't you have a duty to save the members?

You guys were all so lacking that I'm incredibly anxious, but yeah, I believe you guys, I believe you'll hold on.

If I just take a picture of Hwagyeong, I'll tear the sky apart, turn the earth upside down, and end it.

And we have to go back together.

I live, and you live too.

We have to live together.

We could eat together, take a bath exclusively for female members, see the sights of Jungwon, train together, laugh together, cry together. There were so many things I want to do together that I could probably keep talking about them for days.

Yeah. Us.

In an instant, the fingertips wave in the air.

It wasn't the pain that felt like shattering fingers or the sensation of breaking ice like before.

Just a corner that was held so softly.

"Huh?" Qing looks up blankly.

The sky, unobstructed, seems to have risen for thousands of years, yet remains blue. What the heck, where did space go? was there no space in this pseudo-Jungwon martial arts world? was this what my martial arts world looks like?

With both arms raised above the ice wall and my head popped up, a transparent flower appeared before my eyes.

Huh? What was that? What kind of flower was that? was it a congratulatory bouquet?

Cheonhwa, flower of the sky.

Sky. Space. World. The world. Everything.

Three flowers bloom like a halo behind Qing's head.

Samhwachwijeong (Three Flowers Gathering at the Peak).

Establish yourself, stand on your foundation, and perceive the world.

Only when you see the world and understand and embrace the earth will you know where you stand.

Because you exist, I exist, and because we were together, the world exists.

When heaven, earth and man, the three yangs, were in harmony, its fragrance resonates throughout the three thousand worlds.

Thus, a person can control the world with his or her own mind and reach the state of thought.

People revered and respected it, calling it the realm of harmony, Hwagyeong.

Qing climbs up the wall and looks down at the world.

Why was direct advice on enlightenment taboo, and why did Master beat his chest in frustration?

Now I understand.

There were as many worlds as there were people in the world, and the three heavens, earth, and people of Samyang were all three different things, so even if others add to their worlds and spread their own, it was useless and will only be a distraction like a dream.

So I can't speak, but just looking at the pathetic members of our Half-Geom Ssangdohoe, who were all groaning about whether they're at their peak or their peak, doesn't it make me sick?

But that's the thing, if you embrace it with love and yearn for it, won't it work?

Right now, yes. I have to go save the kids.

What should I say, yes. The evolution of the harmony mirror, the super harmony mirror, the heavenly sword was coming!

Qing smiles brightly.

And then, without hesitation, she leapt over the wall.
