\chapter{Crossing Our Blooming Wall (11)}

There were two types of monsters that pass by on the left and right of the blue.

One of them was a group of monsters who turn their heads as if they saw something they shouldn't have seen, scream, and spin around in the distance.

And another group, although they didn't avoid each other, looked somewhat fearful, and even bowed politely when their eyes met.

Qing's eyes narrow.

Well, let's say the former has already been woven in Gwangju.

Are the Blood Cult members afraid of the existence of the West Gate?

Come to think of it, how did the Blood Cult plan to use so many mines?

Even if you control the minions who were gulping and gulping with their eyes rolling back and forth with some kind of means, you won't be able to distinguish between enemies one by one, so there must be a way to make them fight only the enemies of the Blood Cult.

Since I could tell right away without having to use my head, I thought it must be the presence or absence of the Subsimgong.

The kind that run away and make a big distance were probably the blood demons I saw in Gwangju, and the ones that just stare blankly and ask why you came this way were probably a different kind of heart-eating monster.

Then? I'm fine.

Qing, the blood sect master, watches Changsanya closely, and, as if he hasn't noticed yet, he quickly lowers his body and hides himself.

In fact, there was not a single spot that was not in pain, because I was cut, stabbed, and hit to kill my enemies.

There were no medicines, bandages, or needles for the body right now, and it was very strong and not a constitution that was prone to infection.

But isn't there a way to immediately address the damage to the dantian that was secretly aching and the blood vessels that were being crushed by the flow of energy?

The Qing quietly controls the seething dispute.

It was a miracle that unfolds in the middle of enemy territory.

No matter how far you stray from your goal, there was no heart as strong as this.

Meanwhile, the Sapa warriors were isolated like a round island, facing hordes of minions coming from all directions.

"Heart! Fresh heart!" "Just one bite! Just one bite!" "Just a taste, please! I'm so hungry! I don't know how long I've been starving!"

The blood demons, who were full of poison, rush in without sparing even a single body and devour the heart.

When the sword was stuck, it willingly gives up one of its limbs and rushes in, thrusting its blade into the torso and greedily taking the heart.

It was a shameful sight to see them entangled with each other and fight to steal my heart, but it was also an even more spine-chilling sight.

Just like the demons of hell who covet my heart more than my life and want to devour it.

Even jumping up and down, stepping on the backs and shoulders of your comrades, jumping up and down, throwing yourself into the enemy lines, a bold strategy, or to be precise, a mad gluttony.

The exchange rate between the Sapa Muin and the Blood Cult Mine was miserable at five to one or six to one, but the difference in quantity was also like that.

If you just look at the numbers, it seems like the Sapha Muin will be in dire straits and won't be able to last long, but that's not the case.

All the warriors who fall to the mine were just low-level servants.

Even though the number of Sapa warriors was rapidly decreasing, it seems that only the best were being weeded out.

The self-proclaimed Seopsimmagung and the so-called Siksimdan Vice-Chairman Changsanya couldn't help but let out a groan of discomfort.

It was a sight of blood demons melting away, each one created and collected over twenty years.

The completion of the blood demon itself was not difficult.

If you feed it ten pieces of the Great Law, it will be completed immediately. If you feed it one heart, it will be completed in ten days, and it will be completed in an instant.

However, since they were guys who have become increasingly ineffective after receiving their salaries, they were unfinished products that have no immediate use for the Blood Cult, which was still quietly pursuing its great undertaking.

So, I put him to sleep with medicine and raised him with minimal food.

They gradually learn to suppress their hunger and appetite, and if you feed them like that for ten years, they will become true vampires who can perfectly imitate humans.

The male was a blood ramundo, and the female was a beast with a heart, adding to her wildness. They were used as beast hunters, slaves, and courtesans, so they were truly pets that have been raised with great care.

How can we just watch the fruits of these efforts melt away in vain?

Changsanya looks at one point.

The target was the place where the damage from the blood demons was the most severe, the place where the fat guy and the skinny guy were right next to each other.

The fat guy was just blocking the attacks of the blood demons with his bare body. His clothes were already torn and he was barely wearing his underwear, but he was not injured anywhere.

A skinny monk supported him from behind and kept spraying bloody spray. Anyone could tell that he was a master of the secret sect. If he was hit in the head, his head would fall off, if he was hit in the arm, his arm would fall off, and if he was hit in the leg, his leg would fall off. Wasn't this a divine skill of Wulin?

So, with the martial artists people gathered around him, he stood firm and the precious blood demons' corpses piled up.

Then suddenly, hey, why were they only fighting over there?

Where did that Heavenly Blossom Sword girl go?

Changsanya turns her head quickly.

Oh no! Did he run away?

My mind snaps to a halt and my heart sinks.

The Demon King had already lost his daughter, and now he'd lost his enemy? It was obvious that his wrath would surely fall upon me.

"Heavenly Blossom Sword! Heavenly Blossom Sword! Where was that bitch! Find Heavenly Blossom Sword!"

The lower-level blood demons, already blinded by hunger, don't even pretend to listen, but those who were close to completion and have reason react.

To be exact, I just reacted.

Heavenly Blossom Sword? What was that? was it edible? Oh, a sword, a sword? A famous sword? Why a famous sword?

With innocent, bright eyes focused on their master, how could the blood demons, who had just awakened from a long sleep, know what the Heavenly Flower Sword was?

"Damn it, Heavenly Blossom Sword! Heavenly Blossom Sword! That bitch's name is, huh, Ximen Qing! Find that bitch Ximen Qing!"

Ximen-Qing? Who was it? were you eating? Do you know anyone? I don't know. You too? Me too. Wow, I'm here.

Changsanya hits her chest in frustration.

These ignorant little beasts!

"Just do what you're doing! Sweep away those Sapha bastards!"

The window sill soars high, crushing the poor floor with a loud bang.

Changsanya's body, which had been raised high with breathtaking lightness, went up the building, and then went out, climbing from roof to roof, when suddenly, a lone figure appeared in the battlefield seen from above.

Of course, on one side, it was a battlefield with people killing each other, blood and flesh flying around, but when you see a person sitting cross-legged on the outside, it was only natural that your eyes will be drawn to him.

At first, Changsanya passed it off as nothing serious.

I thought he must have died while sitting down.

Of course, the demons wouldn't ignore the beating heart of a living being, so they must have died in that position.

A thought that occurred to me as I climbed over two roofs.

No. If he had died from a blood demon, his entire body should have been torn to shreds and mutilated. Given the blood demon's appetite, which includes not only the heart but also blood and flesh, there's no way a complete corpse would be sitting cross-legged.

Clang, …

So, when I looked closely, I couldn't tell what color the original clothes were, they were covered in blood, and that, that… …!

In that moment, Changsanya exploded.

Not only did you kill Mahi, and then hang all the Sapa bastards there, ruining the twenty-year plan, but now you're calmly treating the situation as if the fight was someone else's business? At this time?

"You bastard!! Ximen-Qing!!"

"Oh. I got caught."

Qing, who was about to explode, jumped up, grabbed Park Do and dove into the blood demons, unleashing a dazzling display of energy.

The lower-ranking blood demons shudder and scatter as they escape, and the rest were cut down without even being able to fight back, and only then does Changsanya realize what has happened.

I, I, that girl, has mastered the art of sub-shimgong!

And seeing that the blood demons couldn't resist, that achievement was no small one!

How can a woman called the Jeongpa Yeohaep be so disgusting! She's still a despicable bird!

Changsanya steps on the pavilion, and the roof shatters into pieces, shooting out like a shell.

As the blue split into eight and fled, a dull explosion behind them sent chills down my spine.

Because it brings back bad memories. Miss, I really hate those kids falling from the sky.

And then, a blood demon suddenly appeared in front of him, blankly staring at him.

What was this kid just looking at? Qing turns around, cutting off the blood demon's neck.

However, I feel a bit awkward because I don't resist.

"That bitch, that bitch was the Heavenly Blossom Sword! Oh, an, Bahal-! Kill that bitch! No, don't kill her, break her limbs, cut her, cling to her and get in her way! This was my top priority!"

Then, all the blood demons except the lower ones turned around and focused on Qing.

"madam."

I was just thinking about it! They say you have a sweet mouth!

"Break my limbs!" "Don't kill the Heavenly Sword, get in the way!" "That girl was the Heavenly Sword!" "Break it!" "I'm going to cut it!" "I'm going to cut it too!"

Blood demons rushing in all at once.

But the intelligence in his speech was a bit? What the? Those who avoided him saying he smelled were just blinded by his heart, but they didn't seem retarded.

Does being obedient decrease intelligence?

Qing takes a step forward, Shinnyeo Sword, Cheonnyeo Great General.

A bold straight line cuts the mine in half.

Although it was not a particularly sophisticated technique, it was a favorite of the Qing because it instilled fear in the enemies through its cruelty.

However, Mine extends his blade without any hesitation between his divided comrades.

The mine that hit the wrist hard was black.

Ding! The broken blade grazed Mine's cheek, leaving a long gash—

"Your wrists were strong! They won't get cut!"

Qing immediately realizes.

These kids have lost their sense of humor!

Do you think that fearless people listen well?

The new Qing form was immediately divided into eight.

The blood demons also scattered in eight directions without hesitation, and as soon as Qing appeared, he was hit in the back, staggered, and lost his balance at that moment, when a blade stabbed his back thigh.

"Ugh!"

The screams of the blue burst out, but screams like "Kwak", "Ak", "Eww", etc. were screams that come out when you can endure it.

Of course, the thigh muscles were the most powerful in the human body, and the thighs of the Qing were the second strongest part of the body after the elbows, which were protected by the small intestine.

"Your thighs were firm too!"

"Foot! I'm aiming for the foot!" "I'm aiming for the shoulder!" "I'm aiming for the thigh!" "Hand!" "Upper body!"

Qing, these kids, they act like idiots, but they're not stupid!

Qing throws his blade again.

In front of the blade that cut diagonally, the blood demon fearlessly stretched out his hand, but it stopped after slicing it in half from the palm to the elbow and below the elbow.

Then, Mine's left hand reaches out and grabs Qing's forearm.

"It hurts! But I caught it!"

It's not that he doesn't feel pain, but he's a blood demon who holds on to Qing's wrist tightly even after his right arm was torn in two.

In an instant, a flash of heat, a fire ignites in my shoulder, and a mine suddenly latches onto my arm as I swing it in retribution. Then, a heavy weight clings to my leg, then to the other leg, and as I cling to it with my arms folded, I hug it tightly.

Each one was nothing special, from first-class to early peak level, but the problem was that these guys blindly follow orders without fear or succumbing to pain.

"You bitch!"

Qing turns around with the blood demon hanging on.

It was like wearing shackles shaped like a person, so my body was numb and I looked up and saw Kang-gi right in front of my nose!

The new form of Qing was straight into eight, hanging four of them on its limbs, and the five new forms scatter, and with a bang, Qing makes an emergency landing, scraping the ground with his face.

A fishy smell and a chilling feeling of moisture running down my nose, and at the same time, a pain that squeezes my brain, a strong migraine that feels like a needle, no, a spear, was piercing my brain, and when I try to open my eyes, the world feels thin, I can't even open my eyes, ugh, I'm dying, gasp.

Hanging one person and using the Neungpa Mibo was enough to give you a headache, so hanging four people was a natural reaction.

Wasn't that also a situation where he was using martial arts that were originally unusable through illegal means?

Qing reaches out and grabs the hair of the blood demon hanging from her leg, trying to pull it away.

The blood demon, who had been holding on with all his might, suddenly changed direction and turned backwards, causing his neck to snap and only then did he lose his strength.

Then, Qing twisted the ball of the guy hanging on his left foot and jumped up, flying high up with the anti-gravity walk of the Moon Girl Walk.

"It flew!" "Interfere with the Thousand Flower Sword!"

Blood demons jumping up and down.

What goes up must come down again, Qing's footprints land on the face of the blood demon who was agape and stretching out his arms!

As the Pacheon Magic Energy surged from the Yongcheon point on the sole of the foot, the demon's head was shattered and the blue spirit rose into the sky again.

The heavy weight hanging from his right hand clenched his fist and struck the side of the blood demon wrapped around his left arm.

The blood demon, whose body was crushed, released his locked arms and fell, and the blue who fell after him swung his right arm wildly and hit the blood demon with a great sledgehammer.

Finally freed from the bonds of the five great bodies, Qing nimbly moves among the mines.

By focusing solely on avoiding, the strange joint bending of the oil-filled limbs, the all-round surveillance of the awakening art, and the slow, trembling movements that contained the secrets of the Muyeongshinsu managed to evade the demons one after another.

Leaning back, he slipped between them, his limp arms slipping as if they were about to be caught.

They run between the enemy's flanks, sometimes slipping between their legs, and then suddenly turning at a right angle and jumping backwards.

The demons collide, fall, get tangled, and roll on the floor.

However, they were just desperate to avoid it.

After all, if the opponent was willing to die, no matter how hard you attack, they will only show an opening, and they were blood demons who will throw away their weapons and try to hang on to the blue limbs that cannot be cut or broken.

"You bitch! Instead of running away like a rat, why don't you come out and stand tall?"

"You're ridiculous! You're asking a rat for a life or death deal! How can an old idiot who can't even catch a rat be harassing a young person?"

It was fortunate that the blood demon's limbs flew up every time Changsanya chased after Qing and sprayed sword energy, otherwise they would have been caught in an endless game of tag.

But I'm starting to feel dizzy and lose my energy.

Even though they were small and minor wounds, the way his limbs look was gone after he's been running wild for over an hour and a half. This blood, it looks like he's lost too much blood.

Did you drag me here for nothing?

I thought it was a brilliant idea that would instantly get rid of the Blood Cult and those damned Divine Exploration seekers.

No, how would I know there would be hundreds of monsters piled up there?

Qing grits his teeth.

Don't be upset, don't be weak.

It's my choice, with evil and with force,

That was the moment.

"Qing!! Get down! Quickly! Ximen Qing!!"

A pleasant bass sound pounded in her ears, but with a desperate appeal.

At the sound of a voice clearly calling out to her, Qing reflexively flew forward and brushed the floor-

!!!!

The earth trembled, the entire building shook and shook off the accumulated dust, a ferocious thunder that seemed to be the very embodiment of the power of a wall.

A roar that shook the heavens and the earth, a huge explosion that went beyond the limits of sound and roughly struck not only the ears but the entire skin of the body.