\chapter{Crossing Our Blooming Wall (3)}

Qing blinked, blinked again.

"Huh."

So, does that mean that someone stole clothes that someone else had made for their lover, even preparing the materials themselves, and gave them to me as a gift?

Oh my.

I felt like the middle and bottom were pinched, and it wasn't just because of the underwear!

Hey, you're such a scary bitch.

Didn't they deliberately prepare small underwear to fool me?

The length was just right, so I thought it was just because the underwear was too small, but it turned out to be a trap.

"You, you…! Can't you take it off right now?"

"Oh. Yes. That wasn't my intention. I just wore it because they gave it to me. Wait a minute, I'll take it off for you now-"

"No need!"

Seopsimmahee screams.

"You want me to give you clothes that someone else wore as a gift? You! Do you think that makes sense!?"

The face with teardrops hanging down was so angry and pitiful.

Qing just awkwardly bobs her head, um, I feel a little sorry about this.

Then suddenly I thought, was this something I should be sorry about?

It wasn't that I stole the clothes because I had any ill feelings or because I wanted them. I'm a victim too, a victim!

Qing glares at Yun Yuanying fiercely.

Regardless, Yun Yuanying just looked at Qing with a bright smile.

It's so much fun I could die.

"Damn it, what were you doing! Kill that bitch right now. No, don't kill her, capture her and make her kneel before me, I'll rip her apart piece by piece."

Knock knock!

With the sound of a door opening roughly, people pour out from the rooms at both ends of the hallway.

The blue head rolls nimbly.

Can you get through that? No, not the hallway. Then, yes, the window.

I have already seen the structure of two rooms.

I was trying to move by digging through the wall and escaping through the window.

what?

Somehow, I don't feel any particular hostility from those blocking the hallway.

"Lee-ik, what were you doing!? Kill this bitch right now!"

But there was no response.

Wouldn't he just stand there, blocking the hallway and watching blankly?

"What's wrong, sister?"

"Oh my. Why were you calling me 'sister'? Can't you just call me 'the stinky bitch', 'the stinky bitch', 'the icky bitch' like you always do? Did you ever call me 'the stinky stinky bitch'?"

"Huh, huh?"

"You have to do your own work?"

Unyeonyoung takes a step back.

And then he smiled at Qing.

"This person was a member of the Blood Cult Mazon King's Department, and was called Subsimmahee Yuryang. Oh, by the way, the Mazon King's Department was a unilateral claim by the Shiksim Demon Army, and was usually called Shiksimdan."

His eyebrows twitched.

"Siksimmagun? That bloodthirsty bastard?"

"To be precise, it's called a blood demon. You're a foolish old man who dares to compare a heart-eating monster to a zombie. And this woman was the only daughter of the Demon Lord of the Sub-Sim Demon Army."

"You! You corpse-slinger, how dare you, you, you little rascal…!"

The flow was loud.

Either way, memories of Guangdong Province and Jinjiazhuang flashed through Qing's mind.

Blood demon.

He was an ugly monster who had even abandoned his natural responsibilities.

A child eating his mother's heart, the most gruesome meal scene in the world.

The voice of a frail mother who protected her child who was chewing on her heart to the end, her eyes that were fading away…

I thought that even the guy who turned people into such monsters had children.

Did that guy have a precious wife?

Would my child be precious to such a person?

Just as a drop of ink spreads in a glass of water, a disturbing color also spreads from Qing's eyes.

The murderous intent that was squeezing her liver and gall bladder, Mahi, who had been hesitating, shook off the fear that was engulfing her body and screamed again.

"What, what was this kid! Yulno, what were you doing!?"

A bloody stream of energy rushes in before the words were even finished.

In front of Qing's nape, the white back of his hand collides with the blade, making a loud, loud noise.

But the arm that was raised absentmindedly to block the iron dagger did not move even slightly.

Yulno, or Yeonyul's expression, hardens noticeably.

"Mama, avoid it!"

With a sharp, urgent voice, the two daggers held left and right draw countless lines.

A dense, blood-red stream of water forms a net and rushes towards Qing.

But since they can't come together as if the middle was torn, the sound of the metal striking each other continues for a long time.

Qing, one step, two steps, three steps.

Slowly back away, swinging both arms.

The locker room door touches his back, but can a mere sliding door stop Qing's advance?

A door that slides over without any resistance was not as effective as a grain of rice as an obstacle.

I think it was Yulno.

How come the person's name was Yulno?

~ was a word used to call a slave, so Yulno means slave Yul.

Since Qing was thinking like this, it means that even though he appears to be stepping back, he was actually very relaxed.

Well, it's actually quite leisurely.

It's fast, but that's it.

No, I guess it's a bit ambiguous to say it's fast.

Because it was such a light attack, the dagger was only blocked by Qing, and bounced far away.

Thanks to that, it only creates a flashy image, but it was a shallow attack that won't even cause a small bruise even if it was hit by dozens of attacks.

Still, the reason why Qing retreated was simple.

If there's a fuss, your face will be sold.

Even without that, there were already several heads sticking their heads out of the room just now to check outside.

Among them, there was also the fat Povidone's head with its generous amount of stairs, so it was said that the village was swarmed with leech-like magic explorers because of that damned magic absorption.

So, I thought I had to fight where they couldn't see me and get back quickly.

But what was it?

Is this really a sword?

It was a strange energy that was too light to be called a sword, but too sharp to be called a sword energy, and stops at a point that was neither here nor there.

Even if Kang-gi follows the principles of Kwai or Hwan, he has a basic sense of weight.

As powerful as the concentrated energy?

That was why a weapon that was swung with a strong energy was much heavier than its original weight and crushes the opponent.

But the attack being blocked now has no such weight.

But the sharpness of the flesh that was gently tapped was comparable to that of a strong sword.

Sharpness without weight was only effective when cutting soft and weak things.

It's not that the dagger of the year was gradually losing its sharpness.

This was because the blade keeps going up and down as it collides with the indestructible, diamond-like minority of the minority magician.

Suddenly, Qing's right hand became strangely bent.

It was as if all the bones had disappeared, as if it were a snake, or a raccoon with countless joints, or a rope that was left on the ground and swinging, so sluggish.

It was an optical illusion created by the meeting of the accomplished Muyeongsinsu and the completed Yuryuyeonryeon training.

In that way, Qing's hand digs in like an earthworm and tightly grabs the back of Yulno's neck.

"Ugh! Ugh, ugh……!"

Qing raises her hand.

Yulno's feet were floating in the air, and he was at a loss as to what to do.

That was the moment.

Phew.

The feeling of a blade digging into my skin was something I've experienced many times before, but it's just as dirty.

Qing glances down.

The blade protruded from between Yulno's stomach and dug deep into Qing's right chest.

A fatal blow that penetrates the center of the rib cage, avoiding it from afar.

"Ugh!"

Qing screams and throws Yulno.

The loud sound of a person falling down.

Qing sits down and clutches her chest.

As the chest of the luxurious handmade martial arts uniform turned red, Qing thought.

Miss, I'm bruised again. I'm going to have to tear off or cut off this damn chest. It's killing me.

In fact, the Qing's self-defense technique has already reached the realm of the unconscious.

Just as the North Sea people can operate the Hansimgong while sleeping, the Qing also generates a sense of euphoria in the unconscious realm beyond their own awareness.

The pectoralis major was a muscle that was embedded in bones and muscles, and the pectoralis major was one of the strongest muscles in the human body.

"Oh. Don't let the enemy know of my death. No, um, um. I knew this would happen if I hesitated…"

Qing falls to the floor with a thud, along with a will that was somehow very plagiaristic.

The cold wind rippled through my skin and made me scream loudly.

Still, thanks to that, I was able to make a pretty complete death scene, even adding the final words.

Across from the fallen Qing, Yulno, whose waist was half cut off, was vomiting blood and pieces of his severed intestines.

"Cough! Whoosh! Mom…?"

"I, I did it! I defeated the Heavenly Sword! Hehe, and with this, to the Lord, hehe."

After that, we see Mahi Yuryang shouting with a big smile on her face.

"Mom, help me, save me……"

"Huh? How could I do that?"

The question of flow may be valid.

Because with the medical techniques of Zhongyuan, there was no way to save a person whose lower abdomen had been cut in half.

But it might be a bit inappropriate for the person who cut off his waist to say that.

"Ugh. Please……!"

"Even if you say that, it still doesn't seem like there's any hope…."

The flow glances at the blue.

And then, somehow, I gulped.

"mama?"

"Yulno was going to die anyway, right? I'll make it easy for him."

"Mom, sleep, gulp! Ugh! Just a moment, I, ugh."

It was a blue disguise of a corpse that died in vain without even being able to close its eyes.

It's a pretty plausible way to play dead.

Surprisingly, this act of pretending to be dead was a true martial art, and in technical terms it was called the "Gwisikdaebeop".

Although it was only a technique of pretending to be dead, it was one of the ultimate techniques of Zhongyuan with an extremely cool name.

From the perspective of a doctor who pretends to be a corpse, and from the perspective of a female doctor who has trained and was recognized as a medical practitioner, this was a very bold and radical treatment method.

What was the source of suffering?

Life! Because we were alive!

Then it destroys life!

Yuryang's hand fell into Yulno's chest.

Yulno convulsed and desperately grabbed his master's wrist, but since half of his lower abdomen was cut off, it meant that his dantian wouldn't be safe either, so what power could the hand of someone who was dying have?

So, as Yuryang carefully took out the heart by carefully kneading the inside of the ribs, Yulno kept vomiting blood.

It was truly regrettable to see that sight.

Why on earth was it that evil deeds never go astray?

I wish I could judge for myself whether I'm a bitch worth killing or not, but what the hell was that little brat?

Why did you take out my heart? What the heck? Why were you putting that in my mouth again? Ugh. It's so hard. Don't eat it.

"Why were you eating it raw? You should have grilled it or something. It's bitter, it's bitter."

"What, what what what, what!"

The flow jumps up like a cat that has been taken by surprise.

The lower body was covered in blood.

"You! How could you, so clearly, so clearly, feel something piercing through your heart?"

"It didn't break through?"

"No! It's definitely stuck, if it's not the heart, then it doesn't make sense!"

"Well, if that's what you want. Yeah. Actually, it's exactly as you said. My heart's been pierced. Oh, it hurts."

"Ha! As expected! I knew it!"

"Tsk tsk."

Qing clicks his tongue.

What? were you a friend lacking intelligence?

Could it be that they ate my heart and made a hole in my brain?

"But, how did you manage to stay so healthy with your heart pierced? Ah, ah! Yes, I get it now!"

What the heck, what on earth do you know?

Why do I keep getting curious about people?

"You, you bitch! You were a jiangshi bitch too! A person can't be okay with their heart pierced! Somehow, that stinking jiangshi bitch betrayed our school! I knew it when that suspicious bitch started acting suspicious!"

Then Qing said, "Uhm."

Mahi yells at him.

"What, what! Why were you giving me that look…!"
