\chapter{Crossing Our Blooming Wall (12)}

It was a truly shocking and earth-shattering roar, and anyone who sees the wrath of heaven has come will be struck dumb and fall to their knees.

However, before Qing could even grasp the situation, a weight was pressing down on his limbs.

"Arms!" "Legs!" "Grab them!"

Blood demons clinging to the lying Qing with a cheerful cry.

Of course, those who block the blade with their hand, and especially with the thickest part of their arm from the palm, would be afraid of the loud noise.

However, even in this situation, the way he was holding on to his limbs and hanging on was clearly an order.

It was when Qing was about to get up and shake off the pressure.

"Still! Stay still!"

Qing again loosed the strength in her limbs.

!!!!

Three loud, howling noises in succession, the air ripping apart.

Where have I heard this before, a cannon?

No, the cannon didn't make this loud a sound.

Long before that, much, much earlier.

A grenade? The grenade was too much, yeah, that time.

When I first met Jang Myeong-rang. That… … .

Hmm. What kind of martial arts bomb was this?

The blues start off well but end up being sloppy.

The correct answer was Jincheonroe.

An ancient grenade with the name "Thunderbolt that Shakes the Sky".

In Wulin, it's called a wall-power bullet, but since if you're caught using a Jincheon-roe, you're guilty of treason, was it a Jincheon-roe? No, this was a wall-power bullet.

"Sword Friend! Are you alright!?" "Young Lady Ximen!"

My ears were ringing with sounds that were too much for my ears to handle, but I can hear the welcome voices that break through.

To be honest, as soon as I heard the name Sword Friend, memories of other voices came flooding back.

First San, this time Geomwoo and Ye.

"Oh, you guys-"

Qing tried to get up, but before he knew it, a bunch of blood demons were stuck to his arms and legs, crushing him and making him tremble.

"Hey, wait a minute, let go, okay? Wait a minute."

"No!" "I can't let go!"

"No, wait a minute, ma'am."

If I lay down looking at the sky, it would be in the direction of my joints, so I wouldn't be able to exert any strength, but since several blood demons were pressing down on my arms and legs while I was lying face down, I was wiggling and shaking.

While I was putting in all that effort, several people were captured by the all-round sense of the Awakening Divine Art.

The weight that had been pressing down on the limbs loses its venom and becomes loose.

When Qing suddenly got up, thinking this was the moment, the reinforcements stood shoulder to shoulder and back to back, and together they cut down the blood demons on all sides.

"Sword Friend, um. It looks really difficult."

"Miss Ximen, were you alright? Blood, blood! These, these things that wouldn't be satisfying even if I tore them apart, how dare you!"

"Yes, it's okay. Calm down. It's not my blood!"

"Seeing you jump up, I guess that's true. Tsk."

It's nice to meet you, but, well, let's start with a warning.

"Everyone, be careful. They're blood cult monsters! They don't spare themselves. No, it's dangerous for you to be here in the first place—"

"Sister! Take it!"

"Hey, Qing'er!" "My lady!"

I turned my head and saw a muscular man, two short women, and a tall woman on the other side.

At the same time, something heavy flew in.

Ah! Qing rejoices and stretches out his hand, but something heavy flies past, only to be caught in Qing's clutches and stopped.

This cool window, above all, has a heavy feeling!

You're back, my Iron Sword!

The Iron Curved Sword can be unfair.

What were you coming back for after leaving me behind, bitch?

Woo-wook, the sound of the moon blade that was already different swept through, cutting off the bodies of two blood demons, and as the spear shaft rotated while holding the blade below, the iron weight severed one of the demons' heads.

"Yes, this was it! Finally! Finally! No, not this. You guys, if you stay here—"

"What kind of guys were they!"

Noh Seong cuts off Qing's words again.

Before you know it, the blood sect master, Changsan Ya, has become unsightly with holes all over his clothes and dust all over his clothes.

Judging by the way the bloodstains spread, it looks like it's full of small scratches.

However, Qing's words were not cut off.

"I told you not to?"

"Why did you come to a place you shouldn't be?"

Peng Daesan responds by cutting the blood demon.

But the voice was really hoarse, what was this, he's really angry…

"No, how did I get here in the first place-"

"I came on horseback."

"The general gave me a war horse."

Qing was shocked.

Wang Ssangryong! How can the General do this to me!

I thought he was a great general! Such a betrayal!

When a noble and swift horse sets its mind to running, it can surpass the speed of a light horse master.

Of course, a horse needs a flat road to gallop on, and if it runs like that, it will soon tire and foam at the mouth.

"No, I'm not asking about the means-"

"Did you think I wouldn't notice if you sneaked out? Even though you like to have fun, you're a certain type of person who can't seem to find a way out. Suddenly, you're saying you want to delay your schedule by a day. That sounds suspicious to anyone."

"Even if someone hears…? I, I don't even deserve to be your friend…"

"No, that's not it! And don't use that, the sword-strengthening one! It'll shorten your lifespan!"

I was offended by the unique ultra-low frequency emission of Peng Daesan, but Gong Sun-Yaoyi suffered suspicious collateral damage.

"I asked the General to increase the security during the night just in case he didn't know. Hmph. As expected."

Qing was shocked again. Wang Shuanglong, again!

By the way, Wang Ssangryong, who heard Pang Daesan's words, launched a night ambush operation among the 23 emergency alerts, so even if Qing was a reserve fighter, he need not be ashamed of being discovered.

Somehow, the face of a cunning man saying, 'Hehe, Mama,' seems to be dimly reflected in the dawn sky.

"Sword Friend! What kind of evil spirits were these!? What the heck!?"

"Aim for the heart and head! Be careful, they ignore defense!"

"Ah! What the heck! Then, isn't now the perfect opportunity to practice the magic of the Emperor's Sword? Come on! Haap!"

"No, guys, these things were really dangerous. They're just monsters from the Blood Cult. Thanks for coming, but-"

"Why don't you ask who they are!!"

"-You guys should step back for a bit-"

"Huh. Whatever you want."

"That's right. That can't be."

"No, this isn't the time to be stubborn—"

"Hey, Qing'er!"

"Miss, I'm going to go."

Friends who were clearly caught in the space perception of the Awakening God Art, Lan-ah, Mo-yong So-jeo, and I-ri and Je-gal-i.

No, why were you all here, stepping into my place without permission?

I put it down after much thought, and then they all came rushing in, and I'm so upset, I'm so upset.

"Hey, Zhuge Liang! Wind!"

"Oh, if it's Hangzhou at this time, it's Northeast-"

"I know that too. Does it change or not?"

"At least it won't change until the day I die-"

"Eight!"

Smoke rises with a delightful "Pong!" sound.

Unfortunately, it was the north wind, so it spread to the south, the opposite side of the estate, that is, the rear, but there were still blood demons who had returned behind, and because of their nature of being absolute command-observant, they were not the type of people who would make the decision to hold their breath or anything like that after seeing the poison smoke.

"Cough!" "It's bitter! It's bitter!" "Huh?"

The blood demons in the rear were noticeably slow and sluggish, and they harden and fall down one by one.

But I'll fill that spot soon.

"You guys! Aren't you going to ask who I am?"

"Hey guys? Can't you hear me? First, back off slowly. I told you, Blood Cultists? They're really vicious."

"Well, you can tell just by looking at this."

"No, what were you all planning to do? It's dangerous! Get back quickly—"

"You know it's dangerous."

"Can't you hear what I'm saying?"

Suddenly, something strong shot out from the side of Qing's shoulder, and from the left end of his vision, a brilliant ice dragon advanced with a dragon trim, striking the blood demon's chest and shattering into pieces.

However, as expected from a pretty trash ice skating skunk, the blood skunk that had been curled up in a ball suddenly rose up and attacked again while spitting out pieces of frost.

Wouldn't the owner of the Ice White Dragon naturally take his place by pushing Nan-Gong Shencai on the left?

"This time, I'll protect you."

"No, even Gunyeong. Who were you protecting?"

"This was Miss Ximen."

"Your safety was what protects me. If I worry about you, how can I fight?"

"You keep doing that-"

"You guys, can't you hear what I'm saying?"

"Shut up!" "Shut up!"

Changsanya just opens her mouth.

Those who ignore people's words were getting angry, no, those young bastards who dare to do so, Changsanya grabs the back of his neck, and in an instant, his anger rises.

"You cheeky little bastards! I'll kill you!"

Changsanya rushing fiercely.

The Unwoldo and the thin sword swung upward and downward, colliding with Changsanya's sword and sending sparks flying.

A single drop of rain, piercing through the heads of Qing and Paengdaesan, creating a sharp, piercing sound.

As Changsanya retreated in shock, a thought flashed through Qing's mind: "Aren't these monsters still after my limbs? If I dig in, they'll all follow me."

"Blue!" "Black!"

Surprised shouts behind Qing's back as he suddenly runs out of the formation.

However, the blood demons' gaze was only directed at the world's most beautiful woman in a bloody state.

At that moment, Changsanya also realized her mistake.

I should have given the order to kill the rest of them, but I was so angry and kept talking that I didn't even think about it.

"Oum- huh."

"shut up!"

Qing swings his sword to block the evil spell.

A blue sword with a sword and a sword with a crescent moon were both serious illnesses, and a blue sword with a giant sword can be said to be a completely different entity.

Both in terms of destructive power and within arm's reach.

Originally, the mantra of sorcery was something that had to be uttered by concentrating and clearing one's mind and releasing the energy from the stomach. However, Changsanya was unable to complete the mantra and jumped backwards, striking the moon blade.

"Kill them! Kill them!"

"Kill him!" "Kill him!"

They follow the words, but they were still bloodthirsty demons who were only after Ximen-Qing.

Thanks to this, the party was able to cut down the blood demons, so they counterattack when attacked, but since they were not the target in the first place, they were not very active.

Qing jumped at him, stepped on the blood demon's head, and went even further, the blade of the moon sword drawing a smooth, soft line.

Moonlight Sword, five seconds. First sight.

You have to see the grass to know the flowers.

The fantasy of a passing moon girl.

The woman in blue walking down the street, Wolnyeo AQing, has such a bright expression on her face that even though she was a grown woman, she looks like a child.

A child who grew up alone on the mountainside and played with monkeys comes into the world for the first time and meets his hairless kin. Everything was so strange that he walks in the shape of the letter Z and cannot go on.

But even if they were of the same race, how can one not be afraid of the civilization of this unfamiliar world?

Still, the reason why Wolnyeo was happy was because there was a man who followed her around and taught her about the world.

The woman came into the world following the man I saved, and only then did she realize herself.

The smooth, hairless body alone was because she was human, not a monkey, and the heavy lump of flesh on her chest was because she was a woman.

Alone, it's just nothing.

Existence was determined by you, not me.

A flower that grows alone does not know that it was a flower, and a flower that has no one to look after it was like a meaningless weed.

A smiling woman, a grumbling man. A cheerful woman, a man snickering as if he can't stop her. A woman giggling frivolously, clutching her stomach, a man simply shaking his head. A woman scooping up food, a smiling man, a woman cautiously putting down her spoon and picking up her chopsticks…

The man who had been following and taking care of Wolnyeo gradually started walking side by side, their shoulders getting closer, and when the man flinched at the sudden bump of their fingers, Wolnyeo reached out and grabbed his hand.

So, the hands were held together.

Suddenly, the sky grew dark, and the hot moisture that touched their bare skins, the man and the woman holding hands, the sticky moans created by their uncontrollable breaths, like the shadows of a fading lamp, as if ghosts were trembling, like angry beasts entangled, wet flesh violently colliding, the sticky clapping sound gradually getting faster, more intense, and rising to an unprecedented pitch, filling the space with moans-

No, what was it?

Why were you putting nineteen gold coins into the image of martial arts?

And the subject was a woman, uh, what was it, ahh. Goosebumps, goosebumps, uh. What was it, what was it, ugh.

Anyway, I read the true meaning of the herb.

This was the beginning of martial arts, the beginning where the first martial arts, the Moon Lady Sword, was born as a martial art.

A strange monkey from the nameless mountains met a man and became human, and then a woman.

The sword that the strange monkey was swinging around cheerfully just for fun was not yet even an uneducated one.

Only after meeting people and dealing with them can you learn swordsmanship and martial arts.

The moon was bent in a strange curve.

It's not like you're forcing it with force to change direction, nor was it like you're swinging it around randomly.

A sticky swordsmanship that tenaciously chases and collides with weapons, like flowing water.

"Oum-" Bang, bang!

"Oum-" Bang! Bang!

"Oum-" Knock knock knock! Kkanggang!

"You bitch! When people talk, stop talking!"

"shut up!"

Qing seizes the opportunity and pushes forward.

This? If I do it well?

"Yes, really-"

"I told you to shut up!"

"Kaaaah! I'll kill you!"

Crunch.

uh?

Qing looks at the sky.

The color of dawn has already turned deep blue.

The voices that sound like screams were faintly heard, each calling me Qing or Ximen, but why were they all so desperate?

For a moment, my breath was taken away.

My chest was tight and my lungs were shrunken and won't open, so my heart was pumping blood furiously, but there was no air to move, and all the components of my body protest in pain.

Oh, suddenly, a spurt of blood shot out, slowly scattering across the dawn sky.

Qing realized.

Ah. I think he hit a big one.