\chapter{Crossing Our Blooming Wall (10)}

Hangzhou was a city that never sleeps, a city that never gets dark at twelve o'clock, a city that never sleeps in Zhongyuan.

But today's Hangzhou was a more fiery night than that.

As they chase and were chased, black and strong energy continuously rise, collide, and clash, sparks fly.

Enemies were coming at you with swords, blood-curdling bastards with googly eyes, and pursuers of the divine spirit were everywhere.

There was a saying, "Dosan Geomsoo."

It means a mountain made of swords, water made of swords, and it was a metaphor for the world being cut down only with malice, and was in a very dangerous and dangerous state.

In the same sense, Wulin was also called Dosan Geomrim.

Even before the reign of Emperor Mucheon, when even the government officials were so impatient that they could not kill each other, their daily lives were like that, when they made eye contact, they would draw their swords and fight.

And still now.

"Stop! You bitch, do you remember the name Yang Seong-jin? You old bastard, this bitch was the one who's talking, huh, talking!"

"Stop saying things like that!"

Qing rushes forward with a roar, bends down and dives low, and his hanging sword soars towards the sky.

Originally, there weren't many techniques for soaring up into the sky in martial arts, so in fact, if you add the weight of the weapon, the downward strike would be much more powerful, and considering the subsequent recoil, it's not a wise technique.

But if you have enough power, it's different.

To stop the force rising from below, even a person with a thousand pounds of strength would have difficulty supporting more weight than his body can carry.

An unknown enemy desperately pushes me down with his blade, but I am repelled by the force of the impact, and both my arms cheer.

With a bang, the pelvis was crushed and the slam was forced into the ground. As both feet rise up into the sky, the trajectory was at its peak and the slam was lifted high into the air.

Covering himself in some disgusting blood, Qing sprays a murderous intent.

But that was only for a moment, as the water sprang up beneath the shadow of the pavilion.

As the sunset-colored river swirled wildly, bodies torn to pieces fell down with a thud, and a few of them ended up stabbing him with daggers.

But, in the first place, it was a blue that was left alone because it was an attack that could be taken after weeding out the dangerous ones.

Daggers piercing the muscles wrapped around the self-defense weapon, even the deepest being about an inch or a finger joint, of course it hurts very much.

Patient, this time it hurts a little.

Pain was my strength, the blue pierces my mind and punishes me, the eyes on the masked assassin's face twist with a grin filled with resentment.

"Ugh, this blade was full of poison. There won't be much time left in four years, so I'll wait."

Qing pulls his hand out. The assassin, whose forehead was pierced with blood, tries to smile, "Huh, kuluck, huh, huh."

Well, that's a shame, but what about the poison?

What was it? A salt-making meeting?

I thought he was helping me by telling me to hide behind a secret wall, but he spewed poison and then switched the antidote and divine power, so I turned the tables and came out.

Then, even after you died and I died, he clung to me tenaciously.

The four main characters look at each other and exchange glances.

That girl was really vicious. Why don't you just go back instead of meddling?

That's right, brother. Since the client was behind, I have no choice but to go back.

He took a step back, looking around vaguely, wondering if it was a ghost or something, then quickly turned around and walked away.

Qing, huff, huff, hoo-hoo, catching her breath, staring at his back for a moment-

Beep! Beep!

"Over here! There's the Thousand Flower Sword!"

Along with the shouting, warriors with red bands on their foreheads swarmed in.

They were the guys called Jeok Geon-cheon.

Qing'er sighs and takes a deep breath.

Yes, the martial artists one speaks with a sword.

When was there ever an easy and comfortable fight?

Maybe it should have been like this from the beginning.

How easy it must have seemed to avoid the military and use tricks to avoid life and death issues.

If it's not a matter of life or death, if it's not military, if several people rush in and take advantage of an opening, wouldn't it be because they still have regrets about giving themselves an opening that they're in this situation?

The new Qing model was eight and swoops down.

Infiltrating the center of the uniformed martial arts uniform, scattering swords, the sound of the bell, scratching, grabbing, piercing, pulling out, and tearing.

Then suddenly, bang! Qing, still holding the sword, slid down, scraping the ground.

Park Do's thick sword body was cut in half. He barely managed to block the attack, but his stomach churned with pain and a spoonful of blood gushed out.

"Norm! Do you dare to disturb our enemy, Geoncheon, and get away with it?"

"Tch, then, does the Divine Maiden Sect look like shit to you!? Why, do you guys have any Hyeon-gyeong masters? Absorption magic? Okay, let's say Absorption magic was good, but do you have any plans to clean up after yourself?"

Qing spits out blood and shouts without giving up.

The master of the Red Heavenly Sword who had shouted at him flinched.

Of course, there wasn't any.

"Dead!"

Qing screamed and stomped his feet!

The master of Jeokgeoncheon flinched and raised his sword, but Qing expanded into eight translucent shapes, flying, crawling, and jumping in all directions. The master of Jeokgeoncheon thought, "Oh no, I've been fooled!"

But the Qing has already entered the rear of the enemy's ranks.

He turns his body around, takes off on one foot, gains speed on two feet, and runs away at a furious pace on three feet.

"Damn it, catch him! Catch him!"

A loud noise from behind.

Qingdo now understands the magic explorers.

The absorption magic was a tank.

That very tank that you were talking about as a joke.

Take out all the available debt and buy a tram.

Then how do you pay off that debt?

You idiot, why worry about debt when you have a tram? Bank? Loan shark? I have a tram.

Once you obtain the absorption magic, you will become a martial arts master, so why should you be afraid of the Jeongsa Daejeon?

This was the best in the world, guaranteed to kill, so I already have the magic of absorption.

In similar terms, it was said that you can just pay it back, which was also a characteristic of those who were already deeply immersed and unable to think normally.

So there was no future for these guys.

No gambler thinks about what happens after losing, so just win.

What if it doesn't work? What else can I do but die?

The connections that mobilize the military, the fact that the female protagonist was the best in Wulin, and the like were all things that were not of concern to the magic explorers.

You stupid kids.

Even if you have the magic of absorption, once you get it, will you immediately become the best in the world and have the world at your feet?

Even after seeing this, I feel like I can just leisurely disappear after obtaining the absorption magic?

If only there was a way to rise into the sky and fall to the ground.

However, those who frequent illegal gambling dens believe that they can win big and still live to see the next morning.

Because the Cheonhwa Sword was just that easy.

Wouldn't it be worth it to risk your life and roll the dice once, with the guaranteed best in the world at stake?

The blue one has enemies hanging from its back.

In fact, if you want to shun it, you can shun it.

But then what?

Are you guys going to give up and back down just because you're being pushed away?

If you gamble and lose a lot, you will be desperate to get your initial investment back.

As the Qing raced along the main road, leaving no room for distance, all sorts of wanderers, savages, and rabble rousers, starting from the Jeokgeoncheon, swarmed behind them.

Since we've already gone around Hangzhou once, there must be more than one or two people hanging around.

Ahead of me, at the end of the street.

A high wall, one and a half high, stretches out on both sides, and in the center where it meets the main road, there was a large gate and a signboard, which was written in large letters as Daehyeol.

Blood Moon!

I was so busy being chased that I didn't even have time to ask for directions, so I went around the city of Hangzhou and finally found the headquarters of the Blood Cult kids.

I see the Blood Moon warriors running towards me and the various types of warriors chasing after them.

The large main gate of the Blood Gate creaks as you were startled and rush inside, and begins to close quickly.

Qing picked up the pace, five steps, four steps, three steps—

But annoyingly, right in front of my nose, a door slams shut, and then another bang, the sound of it being hastily locked.

Qing increases his speed, taking two steps, and then one last step, trampling the ground.

Twisting his pelvis, pushing the air with both arms and sticking out his shoulders, he rammed the perfectly formed iron gate.

bang!

With a dizzying pain hitting my shoulder, my torso was thrown forward.

The iron bolt falls off in its entirety, and with a bang, the shackles bounce off the door.

The roughly opened front door creaked, one side tattered, the other side broken off its hinges.

From the gaping entrance, about four pieces of blue fly out, and after a rough crash landing on the shoulder, three pieces slide down, drawing a long straight line on the ground.

"Ugh, this hurts," he says, but Qing stands up as if he has forgotten the pain.

The pursuers swarm into the manor after him, burrowing between the manor's halls and screaming.

"You damned evil creatures of the Blood Cult! I'll kill them all! Strike them! Kill them all! Don't leave a single one of the Blood Cult's evildoers behind! Don't miss a single dog! Don't miss a single rat!

"Kill them all! Kill them all!" Qing shouted sharply, "Let's subdue the Blood Cult bastards."

The pursuers were on to him.

This bitch was deliberately driving us crazy.

Of course, there were those who believe and those who don't.

But a blood sect? The Blood Ramun was a blood sect?

I heard you were fighting the Sadoyeon combat unit properly earlier, but that had nothing to do with the Blood Cult, right?

Isn't it a bit too much to call everyone with blood ties a blood cult?

This can't be happening! The Blood Clan was a Blood Cult!

I should have known when I was writing the blood test!

Either way, they were pursuers who look around with serious expressions and were on guard against any enemy attacks.

But why? It's quiet? was there no one?

Qing's heart also sinks.

What? Why was no one here?

Surely, were all the kids who fought with the Sado-ryeon kids earlier? Or was it because everyone ran out of the empty house to catch me?

And that was the moment.

-Go!!! What a disgrace!!

A majestic voice heard from the void!

Everyone's eyes were focused on him, and soon an old man opened the door to the main hall of the Blood Gate and stepped out.

The voice contained an unusual history, and the expressions of all the so-called experts in the room hardened.

Did such a master exist in the Blood Clan?

While everyone was frozen in place, the old man opens his mouth.

"I am Chang San-ya, the head of the Blood Clan! Who dares to cause trouble in the Blood Clan's main temple?"

Qing quickly interrupts, thinking this was the moment.

"Shut up! You evil servant of the Blood Cult! The truth was already crystal clear. Do you not know that your leader has the audacity to call himself the Demon King and that he even knows the laws of the world!?"

"Blood sect. What an absurd accusation."

"I've already faced a brazen woman who calls herself a princess, and yet you dare call me a vassal! You twisted and broke my limbs, tore at my flesh to teach me a lesson, and only then did you cry and reveal your true nature! Aren't you the evil servants of the Blood Cult!?"

At that, Changsanya's expression turns pale.

"What did you just say?"

"Is now the time to imitate the Blood Clan? If we examine Yuryang's corpse, traces of that vile demonic power will be revealed! Or were you going to say that this was Yuryang's personal misdeed? Judging by the way the Siksim Demon Lord raised his daughter, it seems he was terribly protective of her."

At that, Changsanya's expression hardens.

The pursuers who had been chasing Qing also realized that the sight of him slowly turning back was not normal.

"Wait a minute! We, Jeokgeoncheon, have only come here to settle our grudge with Heavenly Blossom Sword. We have no intention of antagonizing the Blood Ramen. I sincerely apologize for entering the Jangwon without permission. We promise to provide appropriate compensation later, so we will now withdraw—"

"Om—om‒buuhuum‐‑―‧–!"

The master of the Red Heavenly Sword tried to pull his foot out in a hurry, but before he could finish, a strange sound erupted.

The sorcerer's incantation, as soon as you hear it, you can tell it's a secret.

Crunch! Crunch! Crunch!

Then, all the doors in the building burst open violently, and monsters with bloodshot eyes began to pour out.

The numbers that keep pouring out, tangled and rolling around, were as if they were piled up and piled up in a room.

"Heart!" "I'm hungry!" "Heart! A fresh heart!"

"Kyaaaaak!" "Gyaaaaak!" "Gyaaaaak!"

Monsters running, crawling, and attacking from all directions.

"You blood cult bastards…!"

"All retreat, retreat!"

"There was no escape, no escape! All around!"

Amid the shock and horror of the pursuers, Qing also held his sword tightly and rushed towards the mines rushing towards him.

however?

The procession of mines splits left and right in front of Qing.

"Keeeeeek!" "Kwaaaaak!" "Kkiayaak!"

The monsters were running around the left and right of the blue room, making screams that sounded like pain.

Qing's expression was like that for the first time in a while, huh.

What was it? What was it? Why aren't you attacking me?