\chapter{Crossing Our Blooming Wall (2)}

Hmm. What am I doing?

"Oh my, you're incredibly skilled at bathing. And you even mobilized the military. Was Lady Ximen a noblewoman who served a very high-ranking official in the palace?"

Yun Yuanying made a big mistake.

As I kept doing it, I just got used to it.

Qing gently comforted and washed Mo Yong-ju-hee, who was afraid of water, and also took care of Xue-i-ri, who was unable to move due to a compound fracture after a bad cold.

Moreover, both of the people being cared for were not normal.

Mo Yong-ju had to be treated with care as if she were a weak child, and Xue-i-ri was a patient, so she had to be treated with extreme caution.

Qing was a person who learns anything quickly.

I just quickly figured out how to give the Mojiris a bath.

Yun Yuanying, unaware of this fact, simply gives a meaningful smile.

It was a somewhat smug smile, as if he had figured something out.

There was no obligation for Qing to correct that misconception.

Well, guess what?

Contrary to expectations, the expression on Qing's face as he rubs the foam was extremely serious.

Qing learned the Hwanhee Yoyo Gong from Gyeonpohee.

The Joyful Yoyo Gong was a color technique that induces the opponent to reach a state of joy.

Because even if you were a superhuman, at the moment when you reach the peak of ecstasy and pleasure, your upper body opens wide, your mind becomes dizzy, and the balance of your vital energy was greatly disrupted.

The spirit that would hold the body like that was going out for a moment with its eyes closed, so that Hola Dang could steal the Innate True Energy, or more precisely, the Wonjeong that formed the core of the Innate True Energy.

So, there were two key points to the Joyful Yoyo Gong.

To lead the other person to a state of ecstasy.

I don't want to be in a state of ecstasy.

It was a green tea that has become more nutritious due to its second effect.

And this time, the first effect.

A herbivore that cleverly stimulates the opponent's acupoints with a dark magic wand wrapped around the fingertips. I don't know if this can be called herbivore, but anyway.

Sometimes it brushes, sometimes it presses gently, sometimes it flutters like a feather, and sometimes it glides smoothly like silk.

The spine, the muscle knots, the wavy hem, and the long fingers gliding over the plump flesh.

A delicate performance, as if burning rusted gold.

Turn it gently, apply the medicine as if it were nothing, pinch and pull it subtly, and rub it gently to comfort it.

It was a terrifying sex ball that gradually amplified the pleasure.

But? Why?

Why isn't even a single trace of a ticklish laugh, let alone a single moan, leaking out?

What the heck? This isn't right.

Did Heemae teach me wrong?

No. If it's rare, it wouldn't be strange if there was something wrong, but then there's no way it would be registered in the martial arts department.

Hmm. I should have practiced on Heemae.

No matter what, I don't think that's right.

If you pretended not to be able to resist when Heemae suggested it, you wouldn't have to worry about whether it would work or not.

The Qing plan was this.

First, it was a state of ecstasy, and the mind was blown away to the paradise of the stars, beyond the clouds.

If you were out of spirit, how would you know whether you were in the realm of the living or dead?

A terrifying assassination plan to not miss that moment and wipe it out.

A terrible murderous act without regard for means and methods, and it was the very idea of ​​a perverted murderer.

This was the stone woman I've only heard of, she seems to be frigid.

Damn it, you were the most insensitive person ever?

If he's the strongest person in the world, the one who's making a living, isn't it only natural that he should be third-rate in this regard?

What should I do? Should I teach the Girl's Hwanhee Gong now?

Qing felt a great sense of defeat.

Damn, if you thought it wouldn't work, you should have told me in advance.

Then, since it wouldn't work anyway, he must have filled it with selfish desires.

"Okay. Now it's my turn? Hehe, how can you have such a lewd body? Oh my god."

"Haa. Just do whatever you want."

Qing just sighed deeply.

I was just going to pinch the vital spot, but it wasn't going to be a fatal wound.

And also, secretly, or maybe because she was so obviously a ghostly woman, I had a strong feeling that it wouldn't work out for her either.

Then, I couldn't even try it because I was afraid that I would be banned from military service and told to pass through about twenty cities as a crime of contempt.

How do I deal with this guy?

Qing's innate destiny, his divine power as a slayer of the elderly, was not a power that was only exerted against the elderly.

Although he was able to communicate well with everyone, regardless of age, it was the elderly who were particularly vulnerable.

This was not an ability based on charm, such as stickiness or cheerfulness, or, to put it in terms of electronic entertainment, something like that.

If I had to say, intelligence.

It's social intelligence.

A keen eye that can tell what kind of person someone was much easier than others.

A very daring tightrope walk stemming from that, that is, how far can you go to open up and hit?

It was a very charming social skill that allows you to go in and out of people's hearts without being repulsive, without crossing the line too much.

In that case, where does Yun Yuanying's line lie?

If I had to say, this guy has no lines.

He was an opponent you can treat endlessly.

I've never seen someone this soft before, so I think they'd probably say something like this even if I cut their throat.

Oh my, our Ximen Young Lady, do whatever you want, boy, cut off her throat, what a mischievous girl, hehe.

If so, shouldn't the Qing have already taken control of Yun Yuanying by following the law of strong and weak?

Without hitting it roughly and sucking it?

But that can't be done.

Because I have no idea where all this kindness comes from.

Because I'm a blood poisoner?

So what if I'm no longer a bloodsucker?

It wouldn't be strange at all if his gaze suddenly changed and he slaughtered Qing without thinking.

To begin with, the assumption that he was a bloodthirsty person and would shower him with endless affection was extremely strange.

Perhaps the blood poisoner was just a premise, and there was an ulterior motive to achieve something through him.

What was certain was that this cannot be achieved through any kind of threat or coercion, but only if I sincerely want to help and join in.

I see Yun Yuanying's soft lips as she begins to carefully wipe my body.

Even the way he hums a song in a nasal voice was a sight that was no small feat.

I wonder if my own child would have done this, even if it were my own, as I was careful not to hurt or injure them. No, parents tend to push their children hard to peel off a layer of their skin.

Well then, why on earth?

"What were you up to?"

"Oh my, what a ploy! How disappointing. I was just expressing my feelings, wasn't I?"

"Normally, I don't think it's a good idea to play tag with death, even if it means dying."

Hehe, Yun Yuanying was like that.

"Now, would you please raise your arm? Actually, I regret doing something so pointless. I'm sure you'll understand me eventually, but seeing your face after so long has been so frustrating that I've lost my temper."

"If you lose your temper twice, you'll die."

"So, from now on, I'm just going to let things take their course. I don't think I'll get in trouble for it, just angering you."

It means that if you leave it alone, it will eventually fall into your arms.

What was this certainty, this confidence?

Are you confident just because your face was your type, or seriously, your ideal type?

Huh. Why would someone eat their own face?

Of course, Nyong-i, this guy really seems like he'd live off his face.

Anyway, when you get old, it all comes to an end.

Oh. By any chance?

Are you confident that you will be able to maintain that splendid beauty for a thousand years, just like your Master, who was still very pretty and beautiful?

When you get older, you'll eventually come to me?

How could that be?

Unless you see people as really crippled.

Qing hides her true feelings and acts suspicious.

"Haven't we already had enough of this hatred? It's like it's already been decided. It's not like lovers were fighting over love."

However, Yun Yuanying only gently rubs Qing's arm, lathers it up, and gives a yo-yo smile.

The blue just hangs down.

Era. I don't know.

It doesn't seem like people will change right away.

The hands of Yun Yuanying, who holds the bathing bowl, were incredibly clumsy, but because they were so careful and sincere, it feels like I am slowly melting away.

"Hmm, ummm."

As if noticing the mood, Yun Yuanying's humming became more intense.

I just realized this girl knows how to be so crazy.

Anyway, it's a relief that relieves a great burden on my mind.

I was worried that everyone would be worried since I sneaked out in the middle of the night and left the place.

Looking at this, it looks like things will work out well.

I could just run hard and get back, but, um, should I run again right after taking a shower and sweat? It would be best to just sleep while I'm still fluffy…

Because I treated it as if it were a precious treasure, it took quite a while to wash my entire body thoroughly.

At this rate, it's uncertain how many customers they'll be able to serve per day. Shouldn't they be sold at a high price, limited to the very high-end?

The moment you start thinking about something else, it means that you have already completely relaxed.

In fact, even if you try to stay tense, there's no way around it when the other person was being so gentle.

Rather than taking a bath like that, it was better to take a big bath and come out.

"Whew. It was so much fun. Now, Miss Ximen. was this my present?"

In the bathroom changing room, Unyeonyoung lifts up the clothes she has woven with a large movement.

A set of elegant blue silk martial arts uniforms.

Just by looking at it, you can tell that it was a precious luxury item made of melted gold.

"Ah-Qing, they call her A-Qing because she loved to wear blue clothes. Someone handcrafted her clothes with a deep sense of longing. They wove silk with a thousand threads, boiled indigo to create the dye, and then dyed it themselves three times. Each stitch of that fabric was painstakingly crafted, taking a full year to create this martial arts uniform."

I know what Qingdo Cheonjam is.

If I had to say, it was the king of silkworms, the king of silkworms, and its strings were said to be unparalleled in the world.

Is that a pure, exclusive production?

Even if Yun Yuanying was an unpleasant, suspicious, and evil person, her heart softens when she sees the sincerity in that uniform, as if she were growing rice to serve food.

She's a dangerous woman who might change her mind at any moment, but at this moment, she's being sincere.

"Ahem. Normally, I wouldn't accept this. But I'm feeling brave, so I'm accepting it."

"Hehehe. Okay, I'll put it on for you."

Qing quietly raises her hands and feet and obediently follows the words.

But why were the underwear ready-made and not handmade?

If you're going to get a uniform, don't you usually get underwear too?

Besides, it's a bit, no, quite a bit.

If this happens, my chest feels stuffy, my butt feels tight, and even if I wear nice clothes, they don't feel comfortable.

They say that if you save a drowning man, he'll ask for your bundle. You're a real thief, Simpo. In fact, you're the next Shinto, so you're the strongest thief among the thieves.

"Oh, right. What about the uniform you came in? Will you wash it and send it to me later?"

"Oh my, a uniform? were you talking about that rag?"

"No, a rag. That's a bit harsh…"

Even though it was a cheap, hastily prepared uniform, it was durable and long-lasting, and I wear it often, so it was a military uniform that I am attached to… … .

Where did you buy that? If you buy the same one and wear it for a couple of months, it'll probably look the same.

To be honest, it was a bit disappointing. There were a lot of holes in the mountain because of the traps.

But I couldn't help it since the exchange rate was good.

It was the moment when Qing finished her long bath, grabbed the underwear hanging over her buttocks, and pulled it up as she came out of the locker room.

Wouldn't a beautiful woman with a youthful air still evident, standing there with a maid?

"Hoohoo! Heavenly Blossom Sword. Indeed, one face was half and half, um, kind of cool, no, quite cool…"

A woman of mysterious age blocks the hallway and shouts loudly, then starts to stutter as if something was wrong.

"Mom? Come to your senses."

"Oh, right! You dare interrupt our school's event? You, Seopsimmahee, oh, you!!"

The girl, who had just come to her senses and was about to say something, suddenly raises her index finger and screams.

Qing's eyes narrow.

Whose daughter was this, and she's been swearing at me since we first met?

"who were you?"

"You, you! That dress! How could I have made it! I raised that filthy bug to give to the Lord, I cleaned up all the shit, washed all the cages, measured with a ruler just in case the stitching was off, I stabbed myself thousands of times, stitch by stitch, you, you thief! How could you, how could you, dare, his, my, precious……!"

When a person was very angry and at the same time dumbfounded, he or she becomes speechless and says strange things.

That's exactly what the girl was like.

But when I listen closely, it seems like they're also claiming ownership of the uniform.

"Huh."

Qing looked back at Yun Yuanying.

What the heck? You clearly said that you made the clothes yourself, from the materials to the combination, with me in mind.

Why was the producer Hosooin appearing here again?

Yun Yuanying smiled upon seeing Qing's expression.

"Oh, my. I never told you I made these clothes. I told you they were made with the love of someone I loved. That's who I am."
