\chapter{Crossing Our Blooming Wall (13)}

The blue one fell out, and the back of the head was hit with a bang!

As the torso, still with inertia, tried to continue moving forward, both legs flashed as if doing a handstand with the back of the head on the ground.

At that point, he lost his strength, and his body snapped like a scythe, his knees falling to the ground, leaving him lying face down on his forehead and forearms.

"Arms! Arms!" "Legs! Legs!" "Me too, legs!" "No! You use arms!"

Even if Jincheon's lightning strikes, the blood demons don't care, so would they even care if Qing knelt down and prostrated himself?

In an instant, a huge sword, one chapter long, swept from right to left, the Xianyuan Sword of Gong Sun-Yaoyi.

While Gong Sun-Yaoyi staggered while cutting down four blood demons and scattering, the group blocked the way.

"No, I told you not to use that. Oh, use it, it hurts… It'll shorten your lifespan. Why do you keep using it?"

"Ah! Miss Ximen! were you safe?"

Gong Sun-Yaoyi, who had been looking back with a bright expression, suddenly had a distorted expression and stopped talking.

Well, the state of Qing was so miserable.

A single, oblique cut extending from the left shoulder, across the pelvis, and down the right thigh.

The bright red tissue and the already severed cross-sections were clearly visible.

"Ximen, young lady?"

"Huh. Am I really hurt? It doesn't hurt much. It hurts, but it's okay. I can handle it."

Gong Sun-Yaoyi's eyes briefly vibrate.

Well, if you were to list the words of a man, these would be at the top of the list.

Am I hurt badly? It doesn't hurt much. I can handle it. It's okay. I won't die.

"Hey, Qing'er!"

The child's voice was clear and like a scream.

Somehow, the sound was so clear to my dull ears that it felt like it was being stabbed into my brain, and I found myself frowning without realizing it.

But more than that, I felt a pang of guilt at seeing that face, which seemed ready to burst into tears at any moment. Qing tried to force a smile through her frowning eyes.

"Oh, Lan-ah? I'm fine."

Suddenly, something suddenly entered my mouth, and Tang Lan-ah's finger pushed it in, so I swallowed it without realizing it.

And then, the fragrant scent of herbs spread through my mouth, and my stomach, which had been churning, went down in a much more comfortable manner.

"Oh, what was it? was this some good medicine? I feel like I'm coming to my senses. Isn't it expensive?"

"I, I can't live, you, for this, I, really, you, medicine, hemostatic acid, hemostatic acid."

The little girl hurriedly feels around her body.

The falling rocks and bamboo barrels, some of them round, aren't those poison bullets? Can I just drop them?

It was obvious how desperate and confused Tang Lan-Ah, a master of the art of storing things, was unpacking his things in a hurry to find the medicine he has.

"I'm okay."

"It's okay, you look like-"

"It's okay. For now, later."

Qing gently pushes Lan-ah away, and even in the midst of all this, he holds the Unwol-do tightly in his hand and moves forward.

The little girl reached out and hesitated, because she was in a state where she couldn't grab onto anything and couldn't tell him about the injury.

Reflection.

As the saying goes, the sun was at its most brilliant just before it sets, and this was a phenomenon that was often described in both the East and the West, as people appearing even more powerful and wise just before they die, such as fighting their enemies and self-destructing.

According to the opinions of those in Qing's hometown, the brain secretion was this and that, and the sense of pain was paralyzed.

In reality, how could Qing know what the situation was?

It could be the influence of the Baekpalsura Sword, or it could be the function of the Thousand-Sal Gosung or the Blood Poison.

But what was clear was that the pain was surprisingly bearable and not that severe.

It feels like the world was somehow hazy and very pale, and the density of the world has decreased significantly.

But now I have something to do.

Anyway, these mischievous kids, I left them here anyway, but they don't even understand human feelings.

Why did you set foot in this dangerous place?

You should've checked the spot before you stretched out, you know. You don't even know how precious your life is.

I am grateful and thankful, but.

You guys were so clever… … .

So there's nothing we can do.

The transcendent, transcendent, transcendent, transcendental, super-Qing-nim came forward and said, "Yes, I am the president of the Half-Geom Ssangdohoe. Even if I cannot raise the level, I have a responsibility to protect our members."

Then, suddenly, a back blocking the way.

"Come here."

"No."

It's not no, it's not that you can't.

What was this, the emergence of a new format?

As the blood demons targeting the blue rush in, the ice dragon swirls around and the ice longsword dances.

It doesn't look very appealing to Qing.

Bingryong was a pretty piece of trash and his swordsmanship was poor.

"No, come here? Can you please step aside?"

"no, I do not want."

When Qing changed direction, Xue-i would sense it like a ghost and block Qing with her back.

No, why, if it weren't for Young Lady Mo Yong, who filled in the gaps with her ghostly coordination, this bitch would have died three times in this short moment.

Come to think of it, Miss Moyong was also quite special.

This person has never worked with the members of the Half-Geom Ssangdohoe, but he watches over and takes care of the incompetent Gunyeong, and it seems like he was taking good care of this sloppy bamboo lady.

I still vividly remember the time when I squeezed other people's chests because I was sick, but come to think of it, it wasn't that long ago.

She's already grown up enough to take care of her members, and now that she's matured enough, she'll be a truly perfect woman.

The new blue model slides smoothly down the road.

Xue-i-ra, who was desperate to stop the blood demons right away, tried to block Qing, who was trying to escape to the side, but she bit her lip while blocking the blood demons' claws.

And then, the majestic sound of the temple bell.

Blood spurts out from the elbow of the blood demon who was fighting hand in hand with Zhuge Lixian.

Then, Zhuge Lixian's muscles swelled to twice their original size, and the two arms of the blood demon met behind his back, and then he fell down and wriggled on the floor.

"Thank you, Sister!"

Okay. Please accept me as your benefactor for three lives.

Did I just say it out loud or just think about it?

I'm a little hazy, so I don't know.

The blue one bangs and steps on the ground.

Blood spurts in the frost.

However, Paengdaesan and Nan-Gong Shencai were barely holding out against Changsanya, but they keep retreating, so their lives were in danger.

The two of them were at their peak and can't even win against Hwagyeong.

How can I be at ease like this?

Six seconds of the Moon Sword. Ten swords of Jeje.

Defeat the ten swords of my country.

The Yue Kingdom was a vassal state of the Qi Kingdom, and its tyranny was not ordinary.

The ten best swordsmen of my country, the Ten Swordsmen, enjoy cutting down the people of the Yue state, and harass and abuse women on the road.

The man became enraged and ran out with a sword in his hand, but Wolnyeo caught him, knocked him down, and then took over the fight.

The two swords, one crescent sword, and one thin yedo all work together in perfect harmony, and the mighty energy of Changsanya was invincible. One step, two steps forward.

The moon girl steps forward and faces the heat -

"Stop it. Can't you just sit back and relax? You're so annoying, I can't fight you."

A heavily layered voice breaks Qing's thoughts.

"No, I'm just trying to help you-"

"That's right, Sword Friend. Even if you're Sword Brother, they say men and women were different, and if we were to rub shoulders, it wouldn't work out. It's just a nuisance, so why don't you excuse me?"

"No, what? Don't be so loud—"

"Okay. It's annoying, so get out. Quickly."

The tendon on his forehead snapped, blood gushed out. And his hand snapped!

Kang! The blue iron hammer striking Changsanya's black face.

The wind gushes violently and strikes the innocent earth.

Then a deep crack splits the sheet in half.

At that moment, Nan-Gong Shencai swung his two swords and sprayed sky-colored sword energy, causing Changsanya, whose posture was unstable, to take one, two, three steps back.

Qing tries to help him, but suddenly feels dizzy and staggers.

Luckily, I had something to hold onto, so I leaned on it, and it was so solid and sturdy. What the heck, my forearm was incredibly hard. Like a rock.

As I held on, the harmonious face of Pangdae Mountain appeared right in front of my nose.

Huh. What's the point of just being stiff?

I'm stronger than you, so I'm not completely like a water balloon muscle. It's not that I'm jealous.

"I said it was annoying. Get out now. Now."

The low frequency growling boils Qing's erratic thoughts, and as if that wasn't enough, he starts to cry.

"What? San, you were almost in danger just now? And what's the big deal? How can I be at ease when I'm like this? were we going to have to go to a funeral? Did you set a special day for the memorial service?"

"Should I die or should I die? Don't worry about it."

"What? Why were you saying that now? That's not what I meant. If you die, how much would I—"

"Then, what about me if you die?"

"uh?"

Qing was speechless.

It was an unexpected rebuttal, and the voice of Pang Dae-san as he spoke was filled with a boiling anger that had never been heard before.

Not just a low, childish voice that makes you sound angry, but the kind that makes your heart sink with the hot anger you feel even when you hear it with your own ears.

"It's always been like this. You always try to throw everything away and deal with it on your own when times get tough. What's this mess? You look like a living corpse. So don't be so stupid and worry about others and just mind your own business—"

The sound of the voice suddenly disappearing.

"Me! How could I not worry!? If I were weak and give in, then I would have taken a picture of a flower mirror and flown around, or if I couldn't handle that old man, I almost died just now, and if someone else dies, I… I can't stand that kind of thing, really, I can't stand that kind of thing, no, I won't!"

Then, what comes back was a cold gaze.

Burning blue with anger, but somehow mixed with self-reproach that burned inside rather than out.

"On that subject, you left alone? If you left alone, have you ever thought about how the two people sleeping next to you, unaware of anything, would feel?"

"that-"

"You were laughing and chatting with me until the day before, and then suddenly you disappeared, and if you heard someone else say you were gone, do you think everyone would say they were sad and drink together, saying that some people were going to leave and some people were going to stay?"

"I'm not like that."

"Then you'll feel better when you die. You might just smile stupidly, thinking of your friend's face as you die, but—"

"but-"

"Have you ever considered how the others feel? The misery of being denied even the chance to help, because they're weak, inadequate, and of no use! Because they're a useless burden that you have to protect!"

Qing's stomach sinks.

No, I don't think so.

Just. You're weak. Unlike me, you're not susceptible to infection or poison, nor were you as strong and durable as I am. Nor were you armed with transcendent internal energy and various divine techniques. And I can always run away if the need arises.

But, it was a protest that cannot be expressed out loud.

Because that's what it is.

Maybe, I've always thought of it that way, or maybe I've always thought of it that way.

"Can't you see me die!? Don't you see me!? It'd be easier for you not to see me. Anyone would feel better! Even me! I'd rather see your corpse than die! I'd rather die and see you alive! It's much easier to die in peace than live in misery!"

Ugh, somehow I can't breathe.

Because it's true.

It's a sound that feels so right that it makes me feel like I'm being hit.

"So, go. Don't crawl here like that, desperately trying to get a piece of my mind. Maybe you should borrow a hand from that Tang woman over there and get yourself together. Or maybe it's better to just go. You're so energetic, I bet you can still run away. Without you, we can stall for time and then escape."

Suddenly, a scene from the past flashes through my mind.

\textit{When I ran away with Changming'er and met Chojeoljeong, now that I think about it, I don't understand why Chojeoljeong was so scared.}

At that time, Changming'er clearly set up a shield and hung in front of her while shouting something.

Don't make fun of Changming'er.

Changming'er must have been so resentful that Qing scolded her loudly, saying that she thought Changming'er was just a being who came and went when told and was always protected by someone.

\textit{On that topic, what kind of disgrace was this?}

\textit{I am the one who says that we are friends, that we meet up to play and only part ways when it was convenient for me, and that I have to protect the weak and the ugly.}

\textit{It's a good thing the kids have good personalities, if I were you, you would have beaten this dirty little bastard up and declared a breakup a long time ago, telling me to get out.}

\textit{Seriously, I'm so embarrassed I can't even lift my head.}

"Just a little."

"What?"

"Half-Sword Double-Saber Association! Please protect this chairman! One ke\footnote{14 minutes}, just one ke! If you just hold on for one ke, this chairman will do whatever it takes!"

When Qing shouted, "Yes, yes, Sister!", "Qing'er!", "Young Lady, Young Lady, Young Lady Ximen!" energetic and powerful replies came back from here and there.

Qing looks into the eyes of Peng Daesan.

"Don't mess and behave yourself. If anyone dies, no, if they get seriously injured and become disabled, I'll be so hurt that I'll spend the rest of my life being a nanny. I'll brag I protected San, and end up dying alone somewhere."

"Will holding on for half shichen\footnote{1 shichen = 2 hours. Half shichen = one hour} be enough?"

Peng Daesan raised the corners of his mouth.

\textit{This guy, your skills were only at the Early-Stage Transcendent, but your face is truly the best in the world. Even your face is so pretty, you're a handsome man, a handsome man who surpasses handsome men. It's unfair, really.}

\textit{My face feels flushed. Is it because of the medicine? I think what Lan-Ah gave me earlier was some kind of elixir.}

"You're done with the talk!? Brother Peng! Help! Help!"

Nan-gong Shencai had been rolling around, running, and jumping around, and had blood stains here and there.

Qing suddenly wondered if she could really trust these guys.

\textit{I really wasn't talking nonsense.}

\textit{Just watch if someone die or become disabled.}

\textit{I will not let you go and will hold you close until you guys reach Unrestrained Realm with endless training camp.}

Qing sat cross-legged on the ground.

In the space perception of the Awakening Divine Art, she felt her friends gathered in a tight circle.

She still had a feeling of unease.

\textit{I'm not sure if it's the right thing to do to leave you guys alone, but I have faith in you.}

Soon, the surrounding noise faded away like a river submerged in water, and the spirit of the Qing sunk deep within itself, sinking deep below.
