\chapter{Crossing Our Blooming Wall (6)}

Qing scans the surroundings fiercely.

Yun Yuanying lying on the floor, covered in blood. The women surrounding him as if protecting him.

I wondered what was going on when she was covered in blood, but it turned out that the remaining zombies were protecting that woman after she fell in a bloody battle.

And a weapon, something that could be a weapon.

As Qing was looking around, a sword suddenly flew in and stood quietly in front of Qing.

The blood and yellow oil slightly stained on the sword, ugh, Qing suddenly recalls the pain in his chest.

It was the sword that Mahi Yuryang had used to stab Qing.

It was a typical Zhongyuan sword, somewhat short and sleek for women, with a thin blade that bends easily and makes a sharp sound.

The soft blade may have also played a role in the sword's inability to penetrate the pectoralis major muscle.

However, this sword isn't some kind of divine object that moves on its own and cuts down enemies, so why would it float in front of you and stick out its handle?

Of course, there must be someone who can control the sword.

Qing grits her teeth and lets out a sigh.

I'll give you a black line, so do it yourselves.

You're a real bitch, I won't let you off.

Never leave it alone.

Qing takes up the sword.

Since both the Moonlight Sword, No. 10, and the Iron Crescent Sword were extremely vicious weapons, the infinitely light weight of the new sword doesn't really appeal to me.

What's so light?

Huh. You were not worthy of the Moonlight Sword.

From now on, your name was Skewer, Skewer.

Of course, heavy weapons have their own special charms, light weapons have their own special charms, strong swords have their own special charms, and soft swords have their own special charms.

The appropriate level also varies depending on one's strength. Jeon Seop-sim-ma-hee's sword and current skewer don't seem to suit Qing's taste.

Qing storms out of the bathroom.

Clearly, the situation would have been tense for another half hour or so, but there were two, four, six, seven rascals who had the audacity to step into someone else's locker room!

Four people stand in place, three women were held by leashes and crawl on the floor, um, amazing hobby, no, tastes must be respected.

"Who-" "Mr. Yuryang!" "Krrr-!"

"There's no flow here! Instead, get it! Get it! Get it!"

Qing screamed and threw the huge wooden bucket in his hand.

"Kwak!" "Kwak!" "Ttaak!"

The blood cultists, who have been doused with hot water, dance and compete in the game.

The leash that breaks loose in that frost, three women rushing at Qing at once? Dogs? Both of them, bitches?

The moment Qing, who had his sword firmly in his hand, realized why the bitches were crawling on all fours with leashes on.

Martial arts were a means to deal with enemies standing on the ground on two legs, not monsters running towards you with two feet and two arms.

Low lying monsters rushing in!

A steep leap that cleverly targets the lower body.

It's probably a role that holds the feet and hangs on.

At that moment, Qing's right foot stretches out with great momentum.

The blue's instep slapped the first dog woman's cheek, and pieces of teeth popped out cheerfully.

As Qing turned his body in reaction, his left leg was suddenly bent and pulled so tightly that his toes touched his buttocks, and his muscles bulged like a bow drawn to the end.

Bang! As if a sound was heard, the unusually long legs compared to the body shot out again and landed on the second dog woman's cheek!

Wonangak, left and right swings.

In fact, the Mandarin Duck Dance was not a martial art that mimics the mandarin duck, the symbol of marriage. After all, what kind of martial arts would you create by observing a bird with short, flapping legs? Perhaps a long, slender, and elegant crane would be another matter.

Mandarin ducks always come in pairs, two together.

In martial arts, the mandarin duck refers to a pair of legs extending outward and kicking twice in succession.

Dog women running away, teeth flying left and right.

The last one, the woman at the very back, jumped through the gap!

But already, Qing's right foot was raised high into the sky, the sole of his foot parallel to the ceiling.

Standing on your left foot, leaning forward and straightening your right foot, as if both legs were supporting the sky in a perfectly straight line.

Urrung! Suddenly the sky roars.

The Heavenly Demon King's Rimbo, the One Step Gyeongcheon.

Just one step, but the sky trembles in fear.

Suddenly, the image of a man's back flashed through Qing's mind.

Heavenly Horse, mental parasite, why was this kid acting so cool? Should I catch him and beat him up after so long?

The blue's feet fall off.

With a bang, the dog woman's head crumbled like a crushed cookie, and then a single step that even the heavens feared trampled the floor of the guesthouse, and a black magic circled and spread in all directions—

One. Two. Three.

The floor of the radius halfway up was flipped over and explodes.

The thick flooring shattered into pieces, revealing the skeletal framework of the guest house through a hole about the size of a sheet.

Fortunately, the changing room on the lower level seems to have been set up. Qing jumps down, opens the door roughly, and runs down the hallway.

There were a lot of twists and turns, but I thought, well, I can just keep running all the way to Soju.

Ah. See, my moonlight sword, my golden swords… … .

Even though the gold was for the repairs to the guest house, I really like this Moonlight Sword.

Suddenly, things I left behind start to bother me.

-Where were you, you bitch!? -Mahee!!!! -Heavenly Blossom Sword! It's the Heavenly Blossom Sword! -My absorption magic! Where was it!

Qing suppresses her regret at the noise she hears behind her.

In the first place, weapons were not something you can hold onto for a thousand years, so when they wear out, you just buy a new one.

But who's my sucking magician? Why did you leave sucking magic to me? Isn't that the voice of that fat kid Povidone?

Qing holds onto the railing and jumps down repeatedly.

The most dangerous way to go down the stairs, a regrettable method that seems to go against civilization.

However, if Qing's physical abilities were truly world-class, and his strength, flexibility, resilience, sense of balance, etc. were beyond humans, then it would be worth trying.

So in an instant, Qing was on the first floor.

After bravely navigating the noisy and bustling tables and bouncing off the curtains, I finally escaped!

-What the hell.

My eyes met with a series of martial artists soldiers surrounding the front of the nine-story pavilion.

Qing'er yawned, took a deep breath and stretched.

"……Ah, the night air was really nice. Hmm. Still, was it chilly because it's autumn? Should we go back in?"

Qing was about to turn around, trembling with laughter-

"It's the Heavenly Flower Sword! Grab it! I told you that if you fail, Lord Yuryang will never let you go!"

Miss, it's not working.

And besides, they're blood cult kids.

Well, who else but Heavenly Blossom Sword could there be with three heads in front and behind?

Even the chest was soaked with blood and clung to it, making it stand out even more.

Qing neatly gave up on re-entering the guest house.

It would be advantageous in a melee, but innocent people would get caught up in it.

That can't be, and that's why it shouldn't be.

"Come on!"

Qing shouts curiously.

A beautiful voice resonating clearly under the night sky.

At that moment when the blood cultists ran towards him and took two steps forward, Deeng!!

The majestic sound of the temple bell fills the entire area, followed by a bang, a vibration that shakes the earth.

A slender beam of light penetrates through the mess of things that have just run out, casting a three-pronged crescent moon in the color of a sunset.

What the heck! You told me to come! Why did you come!

Blood cultists may feel wronged.

But everything in the world was always moving, and even at this very moment, it was a moment of a great journey across the stars at an unimaginable speed, so there was no one in the world who stands still.

From this perspective, the act of waiting and the act of running were simply the same phenomenon of narrowing the relative distance. This was proven in Qing's hometown.

And given the origins of the Qing, it might be possible to say that the Qing were not particularly deceitful.

However, the violent swords drawn by the Qing skewer stop here and there and bounce off.

First of all, the weapon was too light.

Because the sword was weak and fragile, with the hard bastards and bloodthirsty monsters mixed in, it couldn't properly transmit the strength of the blue.

And two, ugh, squeak, ugh. I should have tied my chest up and fixed it so it wouldn't shake.

When a huge mass shakes and sways heavily, the punctured area becomes compressed and causes pain.

Qing grits his teeth, and then suddenly, an invisible energy explodes, and his killing intent soars.

In that moment, Qing's pupils were torn vertically.

A sinister hue that seemed to split blue eyes in half. With a wildness like that of a beast. Because, wounded, they were even more dangerous, and that's what beasts are.

The Baekpalsura Sword. The first. The Forbidden Blood Wolf.

Don't corner a wounded wolf.

The sight of the blue fangs snarling and bared was somehow incredibly creepy.

The Qing sword draws simpler lines.

A canine tooth that persistently calls for blood, grazing the nape of the neck, tearing the skin off the stomach, and spurting out the contents, grazing the limbs, only cutting through the large blood vessels.

Thanks to that, what rises was blood, and what pours down was also blood, gushing out like a fountain, shooting out like a squirt gun, falling in clumps, and flowing thickly.

"Kill him!" "Damn it, where the-" "Here!"

At some point, Qing lets go of the sword.

Both arms were outstretched, and the head of the Blood Cultist was between them! Blood spurted from every orifice, the eyes dangled, and a desperate scream rang out.

The source of the screams changed from left to right, right to left, and people grabbed each other by the ankles and swung them around, bumping into each other! Crunch! Bang!

It was like a wolf burrowing into a flock of sheep, and before you knew it, you were covered in blood.

Is this what it looks like when a mine runs wild?

But there was also a lot of blood in the Qing.

The image of the Baekpalsura Sword beast, which turns pain into strength and pain into gentle pleasure, comes with a serious side effect of making one rush forward without sparing one's own body.

If you abuse it, it can open your eyes to certain tendencies, but if it's a personal hobby that doesn't harm others, it's okay as long as you don't spread it widely.

Still, the flow rate of Seopsimmahee did something.

Even a thread of heavenly sleep, which was as powerless as a thread in front of the sword, cannot stop the strong energy that can cut through rock and steel, can it?

Still, Cheonjamsa was the king of fabrics.

It blocks even the weakest swordsmanship.

Even if the sword energy that would normally have torn apart several skins was just a whack from a whip, it would have only left a long bruise.

There's nothing you can do about the wounds here and there.

Because the original nature of the fabric was that it was powerless against penetrating forces, it was bound to split open and create holes.

That was the moment.

"Kyaoo!"

Behind Qing's back, a blood demon jumps as high as his calf, as if flying.

With a unique roar, he bites Qing's calf, then wraps both arms around his shins and holds them tightly, locking his arms.

Qing, oh no, a fake sword was flying towards Jeongsu-ri while Qing was staggering. Qing blocks the sword with her wrist, and this time, ahh!

They were running around on all fours, and then, as if they had lost their minds, they started making all kinds of animal cries like "uh-huh, oh-huh, gurgling" and several blood demons flew in at once.

What kind of blood cult was this? Isn't it the Beast Palace!?

One on empty legs, one hanging on to the forearm and biting the wrist, one biting the shoulder and hanging on - and it stings!

Qing's surprise!

What a bitch biting ass!

I was so shocked that I was dizzy and confused, and I gasped, gasped, and got goosebumps!

He was so surprised that the Baekpalsura Sword's image was broken, the beast's pupils shrank, and even the ominous murderous intent of the Thousand-Sal Gosung disappeared.

It was so bad that all my strength drained away and my whole body started to cramp up, and even my nerves gave out, and the beasts' teeth snapped!

"Ugh!"

Qing staggers in the burning pain, and then a pack of beasts rushes at him.

The spatial perception of the Awakening Divine Art reads the flow of the atmosphere, so six were running with their limbs outstretched, five were elegant female bodies, one has a flat chest, oh, long hair and a rich flow, the remaining one was also a woman, wait, why were all the beast imitations only women?

Is this what the Blood Cultists like? You dirty bastards!

Then suddenly, the image of a man wearing a leash like an animal flashed through my mind.

Ah, right. Now that I think about it, it makes sense. It's certainly the right aesthetic decision.

And then there's the commotion!

The blue was crushed under the women.