\chapter{Crossing Our Blooming Wall (4)}

Qing looks at Yuryang's young face.

A strange sight: a pretty girl with blood all over her mouth, dripping drops of blood.

The heart held tightly in the hand, a sagging piece of meat that has died and was now a bonus.

Hmm. Just by looking at him, you can tell he's my precious child.

I've seen this type countless times.

Because I probably grew up in an environment where everything I encountered went my way.

To him, everything I say must have been true.

There was no doubt that calling Nyeonyeong a smelly, suspicious, and unpleasant slut was a fact.

Of course, that's true, except for the smell, but as they say, even a broken clock was right twice.

And it would be natural for him to think that the surprise attack that failed to penetrate the muscle and pierced the life of his innocent subordinate, and even more precious, his breast, would be transformed into a fatal blow that pierced the heart.

When Qing woke up, it wasn't because his heart was intact, but because he was a zombie, he thought he could survive even if his heart was destroyed.

Because I have always been the center of the world and the truth.

So whose fault was this?

What if everything surrounding me was just like, "Oh yeah, oh yeah, Mahi? Who am I to be called a princess? Anyway, everything the princess said was right. What if they clapped their hands and pronounced, 'You're right'?

Suddenly, Qing'er picks a pick and makes a rustling sound.

Of course, that doesn't matter.

The important thing was how to kill this monster so that it becomes known that I killed her well.

Well, how can I get them to regret being born and existing and beg me to kill them?

What should I do?

How about stripping completely naked, grabbing her by the hair, and taking a spin around Hangzhou? Wouldn't that be so embarrassing you'd want to die? I heard some people were into it, so I can get a proper kick out of it.

Well, no, what if that guy was surprisingly sweet and hugs your wounds?

Then, ah! Bring some beast with you.

No, that won't work.

It's a good idea, but it could cause serious harm to innocent people.

What if the Blood Cult kids take out their anger by saying things like, "How dare you peek at our princess's filth!"

Because innocent people shouldn't be harmed.

So then, what should we do?

Qing takes a step forward.

The flow of the Seopsimmahee stopped, and he took a step back.

He looked obviously scared.

Well, anyone who sees that sight can't help but be scared.

The blue eyes glow with an ominous color, creating a lasting afterimage.

The trajectory of murder and evil spirits left in the space itself.

"Oh. Don't come! That's right! You, you, you rascal, you think you'll get away with this? If Abama knew, then yes! Get rid of that monster right now and admit your mistake right now. I-I'll forgive you right now."

Unyeonyoung doesn't even pretend to listen.

Just look at Qing with a gentle gaze.

"Oh my. Miss Ximen. You're truly magnificent. Even though I'm not a celestial being, I always thought the world was cruel to me. But maybe that wasn't the case? Hehe."

"You! You rascal! Why don't you stop now? Yeah, right. I'll pretend this never happened, so just stop that for now."

Surprisingly, the amount of generosity was the greatest generosity I have ever received in my life.

Mahi was someone who has never once endured anything.

What a kindness to turn a blind eye to something that never happened!

It was truly infinite, like the sea!

So, that means you haven't come to your senses yet.

Qing takes another step.

Should I hang it upside down like I did during the green forest?

But that would take too long.

Even though she's a half-assed, crippled bastard, she knows how to imitate strength.

If you hang it up, it'll just be like making you bend your back and work out your abs all day.

If you break the Danjeon, well, you're still a girl on the outside, so if someone sees you, they'll try to let you go.

Miss, should I just kill you now?

I hope you suffer for a long time.

"Get out of here! Get out of here, yikes."

The flow glanced back.

The one who made a great surprise attack by cutting open the stomach of my subordinate was nowhere to be found, but a coward who was just trying to run away in fear.

Of course, it was much wiser to run away than to rush at an enemy you cannot handle.

But only if there was a way to escape.

Before I knew it, the locker room hallway was filled with women, and the group of Yun Yuanying's zombies were blocking the exit route without expression.

"You, you, you rascal! What were you doing! Can't you get rid of these monsters right now!? Do you think my dad would be okay if he found out?"

"That's a bit tricky, isn't it? Mom?"

The instantaneous flow rushes towards Yun Yuanying.

For a moment, Qing was dumbfounded.

What? I'd rather choose death?

What made you believe that you were running towards that real monster?

Well, to Yuryang, Yun Yuanying was just a technician who knows how to make jiangshi.

It's bound to be much easier than the blue one that emits starlight from its eyes.

The flowing body stops,

With both feet in the air.

He stands tall in the air in a very dynamic posture, with his front legs bent and facing the enemy, his hind legs elegantly extended, and his sword drawn, his eyes rolling around with a bewildered expression.

"Huh? What, what was it? How- uh."

"Oh. Was I easier?"

The spine of the blue was cool.

The art of picking up objects by striking the air was a life skill of the most skilled masters.

The Master also uses it to bring swords, whips, or stationery from far away places.

Is it possible to completely capture a person in mid-air with a swordsmanship technique, and even a master using a fake swordsmanship technique?

He frowned with a tired expression.

Is that the dignity of a final boss?

How on earth do you win against something like that?

Regardless, Yun Yuanying casts a warm gaze at Qing.

"Miss Ximen, would you rather handle it yourself? Or leave it to me? Even if you do, rumors will spread that Heavenly Blossom Sword killed Mahui. Then, the Blood Cult members will probably be quite angry."

"You were thinking the same thing. I'm going to go around saying that Nyeonyeong killed that guy and framed me for it, too."

"Oh my. You too, Miss Ximen. It's true that the Blood Cult members were stupid, but they're not foolish enough to believe that. How could a weak shaman harm a demon who has taken thousands of hearts?"

"Actually, he pretends to be weak, but in reality, he's in a life-or-death situation. You could say he's just a zombie hiding his strength."

"A life-or-death situation at twenty-five? That must be truly astonishing. Hehe."

Even if Qing thinks about it, it's something that even a dog wouldn't believe.

Qing's fist trembles.

What a humiliation!

It doesn't work with martial arts, and it doesn't work with words.

Even if you grab her hair and slap her cheek right now, it seems like you won't be able to scratch the inside of her, so wouldn't you be the type of person to just laugh it off and say, "Oh, Miss Ximen, your hands were very delicate."

I wouldn't have accepted it in the first place.

Well, Qing just gave up completely.

Shouldn't we be thankful that the final boss isn't hostile?

Strategy post, you saved my life again today. I hope you live a long and healthy life, and that your work brings you a lot of money.

"Or was there another way? How about letting Seopsimmahee go like this? Then Seopsimmahee will tell my father, and I'll be kicked out of the Blood Cult, right?"

Let me go? Huh.

Of course, if we let it go, Yun Yuanying will be kicked out and the blood sect might fall into strife.

But if she's the bitch who ate thousands of human hearts, what about the innocent people who will die in the future if she lets it go?

Are you saying that you should let a serial killer who was clearly going to commit murder go free just to make him more evil?

That can't be possible.

Because that's not right.

Such monsters must be killed while they can, and must be killed so painfully that they will regret ever having lived.

"Okay? Hold on tight to him. First, wake up his danjeon."

"Okay. Wouldn't it be easier if we did it this way?"

The limbs of the river spread out in all directions.

The only resistance was a suppressed "eung" sound, and I was floating in the air, unable to move even the slightest bit, wondering how they were holding me back.

Even raising it to a position where you can reach out and touch the lower abdomen.

Qing places his hand on Yuryang's dantian.

After carefully feeling inside, Qing was soon able to figure out the cause of the fake sword and the half-penny's strength.

Because the danjeon does not expand infinitely, as internal energy accumulates, it becomes compressed and settles into its pure nature.

But look at this?

It was a form of internal energy that covered hundreds and thousands of different types of energy like a blanket and squeezed them tightly together.

How can you properly emit strong energy with energy that was not properly condensed?

However, it was probably just a matter of time.

The miscellaneous energies would be the bets that were absorbed by eating the heart, and the bet that wraps them all up and squeezes them would be the true body of the Subsimmagi, the inner spirit criminal.

The flow was one in which the suppressed and crushed energies gradually lose their original color and join the flow of the demonic energy.

If given enough time, the thin, flimsy magic of the present will gradually grow thicker and stronger.

Isn't this a structure that ultimately restores purity by increasing the squeezing pressure and accelerating the absorption rate?

Hmm. As expected. I shouldn't let this girl live.

It was the moment when Qing finally broke down the wall of Dantian and burst the balloon of the still-condensed energy of the Subsimmagi.

"oh."

The blue makes an ominous sound.

"Eww! Eww! Eww! Eww! Eww!"

The flow desperately lets out a suppressed moan.

After all, breaking the danjeon could be considered a type of surgery, so shouldn't sounds like "Oh, what?" and "Huh?" be absolutely forbidden during the surgery?

Fortunately, the reason Qing was surprised was not because he had made any mistake.

I was just surprised.

Because the dantian was broken, the true energy that should have naturally dispersed began to rush from Mahi's lower abdomen, through Qing's palm, and along the sixteen transcendental energy channels that had been opened.

It was a blue that absorbs all internal energy in an instant.

He devoured it wholeheartedly, without wasting even a single drop of the spirit or grain of rice.

Indeed! was Qing the very embodiment of the human pig, who not only eats food but also devours other people's vital energy?

No! Even pigs can't eat this much.

So from now on, instead of calling the year of the pig "Qing", we should call the pig "Qing". It's the year of the ox, so it's called "ChukQing".

Of course, that wasn't what Qing intended.

What? Why? How come? I just broke my dantian, so why am I getting this energy?

Qing temporarily registered the Subsimgong, and in the process of destroying the dantian of Yuryang, he perfectly understood its flow and principles.

So, something cosmic might have judged that he had learned martial arts.

By any chance, this bitch? Could it be that when you're on the verge of death, you've forced yourself in by guiding the energy that's about to scatter after losing its owner?

Or maybe some will was at work.

Perhaps it was some romantic coincidence that the spirits of those who had their hearts stolen so far moved to respond and lend strength to my master's avenger.

But Qing doesn't know.

However, I knew very well that now was not the time to sit cross-legged, observe my inner strength, and reason about cause and effect.

"Hmm, I feel uneasy. Why don't you bring him here?"

"Haha. was that so?"

Qing from the locker room to the bathroom.

In high-end bathhouses, there is, of course, a wooden bath for boiling water, and it was used to control the temperature by pouring boiling water and mixing it.

Qing skillfully lights a fire in the stove under the still steaming hot water and throws in the firewood that has been provided.

"Oh my. Peng-hyung, was that Peng-hyung? Oh my gosh. Hehe."

"Ugh! Ugh! Ugh!"

At the word "Penghyeong," Yuryang tries hard to scream again.

Well, when we say 'boiling', we mean the punishment of boiling alive in water or oil.

Before long, the water starts boiling.

Since I just got out of the bath, if there were still sparks left, it means the fire went out not long ago.

"Okay. So, can I just soak it now?"

Qing shakes her head at him.

"No. Just leave it in. Leave the head alone and submerge only the body, then count to three and pull it out. Do you know what I mean?"
