\chapter{My Prison Experience (3)}

On New Year's morning, the first meal was honey rice cake soup.

It was the same last year, but honey rice cake soup?

Honey rice cakes should not be put in beef broth.

An atrocity that cannot be forgiven by human standards!

It really won't work, um, it definitely won't work.

But, the more you eat it, the more mysterious the taste becomes.

It was not for nothing that it was the representative food of the Lunar New Year.

No, but that's not true. This isn't true.

As a human being, isn't this a monstrosity that I can absolutely not tolerate?

Qing only ate two bowls as a protest, which was practically nothing, so this should have been enough to sound the alarm on the food culture of Zhongyuan.

After having a very simple breakfast, Qing headed to the Repentance Hall in the corner.

But, huh? It's not a cave, was it?

Those who were imprisoned may regret their sins, but they do not feel sorry for their sins.

So, there was no repentance in the repentance hall.

It's not even a cave.

Isn't this a total goddamn empire?

At first glance, the only window was a small one just above the head.

This structure was either a toilet or a prison.

A Taoist monk wearing a Kunlun sect uniform was standing guard at the entrance. Since it was a detention facility, there must be a guard there.

But isn't the guard actually standing in front of the entrance, holding a book and absorbed in reading?

When Qing approaches, he was just absorbed in his book, so Qing quietly tries to talk to him.

"Excuse me? Master Danlun?"

"Wait a minute.  I just need to finish this part."

It's not that he didn't notice Qing's approach, he was just thinking, 'You come, I'll read'.

About half ke passed like that.

"Your luck will be good. Starting the new year with a rite of passage in Repentance Hall? It's like exorcising a great deal of bad luck on the first day of the Lunar New Year."

"Can you really be so halfhearted in your role as a guard? You wouldn't know if someone escaped."

"There's no need to worry about that. After all, they're criminals who've had their dantian broken and their meridians severed. Their strength are inferior to that of commoners, so they can't even run. If they can escape, I'd praise them for their bravery and let them go."

"Huh."

"The Repentance Hall is a place where evildoers whose sins have already been clearly revealed are imprisoned and for which it would be better for everyone to isolate them from the world."

Danlun Zhenren points with his finger at the brick building on the other side.

"That's the Tamjodong. Among the criminals in Kunlun, those whose crimes haven't been clearly proven stay there."

About nine out of ten of those who were caught claimed their innocence.

Since it was impossible to just completely broke the dantian and cut the meridians to make them docile, it was necessary to investigate for up to five years to determine innocence.

If there was no conclusion after five years, they have no choice but to let it go.

If the sin was not that serious, the person may be released after breaking the dantian to ensure that there were no side effects.

What if the heinous crime was clearly revealed?

After being made docile through appropriate treatment, they were permanently quarantined in the Repentance Hall.

"It was not about confining and isolating the wicked, but rather about not creating a single innocent victim."

"Well, I understand, but it's a hassle."

Qing was easily convinced.

Of course, he doesn't have some kind of omniscient power that makes him see his own evil deeds, and occasionally even his past evil deeds.

The mindset of not creating an innocent person even if it means letting the wicked go free may be natural for Taoist masters.

"So, there's no need to worry about being sent to the Repentance Hall. They're more vulnerable than ordinary citizens. I've made the beds myself, but if you don't like them, you can come out around noon and return to the guesthouse."

"Can I just come and go? It's a complete experience of life, a true experience of Repentance Hall."

"Experience? Heh, heh, heh, you, you have a knack for making people laugh with just words."

The single-minded Taoist cannot help but sniffle, his characteristic laugh sounding like he was gulping down a large amount of snot.

"Don't worry, I'll bring you food when it's time. I've received a order from the Sect Leader to prepare a sumptuous feast. The door won't be locked, so if you're feeling a bit stuffy, you can come out and get some fresh air. Ugh, this was truly a treat."

Then, the single-wheeled Taoist monk opens the iron gate of the chaplain's office and goes inside.

Upon entering, I saw that it was a fake iron gate with only iron plates added on top of wooden door. It seemed to have been decorated to give a sense of oppression, as it was a facility.

A wide open hallway through the double doors.

"What, there's a newbie!?"

"Ugh, those Malko guys have done it again."

"Welcome to hell!"

As soon as I entered, there was a roar of support.

Then, the Taoist monk Danlun said a word.

"Shut up. You look like you're starving. It's Lunar New Year, so they're going to have a special meal."

Then the room became as quiet as a mouse.

The threat of not being given food was a very effective remedy.

"Here. Come in. Then. That's it."

The single-minded Taoist nods slightly and then quickly walks outside, out of the Repentance Hall.

This was how the real Repentance Hall experience begins.

Qing takes a look inside the confession room.

The wall was made of bricks in the shape of the Chinese character for "冂", and the left and right halves were surrounded by iron bars, and the door has a Chinese character for "凵" ​​carved into it.

A long curtain was placed across the middle of the room to hide it from view.

Oh, no way. Is that a toilet?

When Qing looked closely, it wasn't just a toilet.

It's not just a bedroom/toilet.

There was one luxurious bed that does not fit in the prison cell.

There' also a metal lid in the corner between the bed and the wall, so it was obvious what it was used for even without opening it.

Unlike the cells she had seen on her way here, this one was extremely clean.

Even the bed was a new, high-quality product.

This meant that someone had to carry it here.

\textit{I don't know who you are, but I feel sorry for making you work since dawn on New Year's Day.}

Qing first lies down on the bed.

It was a nice bed, though a bit small, as it was soft and fluffy.

Qing opened the Secret Manual in her arms and looked at it, engraved with the eight characters "Mansangyeoiltaeilhoeui."

As confirmed by the martial arts window, it was the Mansangyeoilsingong, the inner strength method with a purple border.

Let's see, breathing, along the spine, in the heavenly body, and in the middle of the body…

"Hey, newbie."

If you think you'll always have the emergency kit in hand, you don't even need to bother with brainwashing.

If you recite the sutras while turning as instructed, you will soon become proficient, and if you practice consistently while in the meditation hall, you will be able to do it.

"Hey, was this chewing on words?"

Um, Danjunghyeol, where was Danjunghyeol… … .

Gradual light, northward advance, sleeping dragon, um, I'm confused. Where was sleeping dragon? Was it the inner window?

"Hey! Newbie!"

Wouldn't someone be yelling?

"WHAT?"

"What was it, woman? Are you a woman?"

Oh my goodness.

If we do this wrong, it could lead to a huge explosion of sexual harassment.

It's what my friend says, for example, Xue Ga-nom, or Xue Ga-ryeon, or Xue Mo-ssi, or Mo Ga-nom-ssi, but since we know each other's faces, it doesn't matter what we say.

If you're close friends, you can make some dirty jokes, right?

But it's a bit much for someone who doesn't know to do it.

Of course, it doesn't feel dirty or disgusting when a guy flirts with a guy.

But I didn't intend to let them talk nonsense, so I thought maybe if I caught one of the kids who was acting a bit too harsh and beat him up, things would quiet down.

This was when we need an example.

It was a time when I was so anxious about whether I could catch just one person with such ominous thoughts and the will to act on them.

"Those Taoist priests were even trapping women. Oh, right, rookie, how did you end up in the gutter?"

"Wasn't she like the world's greatest witch?"

"Don't be so picky and just tell me. You're going to hear my voice the rest of your life anyway."

But not really?

What the heck? Don't these guys who get stuck in places like this usually just go crazy over women and try to fuck them without even looking at their faces, just because they have long hair?

Qingdo was a proud man who once served in the military in his hometown.

I know that if you put peppers together, their eye level will drop to the soles of your feet.

If you have long hair, or even short hair, you'll look pretty.

Even men who were not usually interested in women become fascinated by them, and even those who have idolized Japanese or Westerners as singers their entire lives become fascinated by young female singers.

Of course, it will be restored to its original state after military service was over.

But the criminals who only speak to Qing with their voices simply ask why they were arrested.

It's also strange to ask why there's no one here who's complaining.

By the way, do these guys know I've been captured?

Haven't you seen the beds filled with luxury items?

Suddenly, a wicked smile appeared on Qing's lips.

Maybe it'll be quite fun for five days?

"Me? I just cut off the limbs and hung them up because those lamas were talking nonsense."

Qing stealthily lowers the needle.

Moreover, surprisingly, it was a fact without a single lie.

"Look at this bitch? She's acting tough. Do you think hanging a few barbarians was something to brag about?"

"Pretending to be strong? I hung twelve lamas. There were four more, but they died before I could hang them, so I just threw them away."

"Huh. Only sixteen? This body was that famous short-lived swordsman. Those who died by my hand were far more spirited than me, yet only sixteen?"

"What kind of short-lived swordsman was that? He was caught doing some swordsmanship in a rural village in Gansu Province, so he ran away to this village. He's a bastard with a lot to say."

"No, King, were you saying that in front of a newbie?"

"Haha, there were so many notorious demons in the martial arts world here, and only one local sapa thief."

Oh my.

Qing's eyebrows twitched.

What were you bragging about?

"I am the Dark Knight. The entire Zhongyuan has been chasing me, so you've probably heard my name."

"Night light too!"

Qing tried to match the rhythm for a moment.

"What's with the dark night light? Even so, he's just a bastard who robs civilians. His true nature was that of a black viper."

"Black Viper!! Huh! How could this be!"

Could it be because Qing's reaction was satisfactory?

Then, as if they had been waiting, countless boasts unfold.

Suddenly, the atmosphere was one of national crime bragging.

These were the guys who originally gathered in an isolated place.

In an isolated place like this, where there was no way to go outside and check, everyone was bound to burst out in lies.

Why, at the beginning of my military service, even at the training camp, wasn't it like that whenever a topic came up?

While serving in the military, the world's greatest electronic gamers, who had made a name for themselves in the world of video games, miraculously gathered in our dormitory.

When we talk about living well, everyone starts off by buying real estate from a young age, and their parents own several factories and drive expensive cars, becoming wealthy.

On the other hand, if you tell a story about a difficult past, wouldn't everyone turn into victims of an unfortunate childhood that they can't listen to without crying?

But since there's nothing else to do, why don't we have a contest to see who's worse?

I sat there shaking like a fool.

But how?

Doesn't this sound like a made-up story?

How did you kill a person?

A man who eats human flesh describes the taste of human flesh.

There was even a guy who told a very detailed story about how he burned down a small sect.

Well, these were really twins.

What's interesting was that there seems to be a hierarchy among these.

Wouldn't it be more likely that the more heinous the acts outside are, the more they will be recognized?

If you listen closely, it seems like they're both claiming to be worse off than each other.

It's so refreshing. It's so refreshing.

The voices were all so husky that it seems like they were really worth living for.

They say that wherever people live, they were all the same.

The sentence for repentance was life imprisonment.

So, it seems like he gave up everything and decided to live here forever.

Are you so excited that you start talking to a new employee?

Doesn't that mean you have the luxury of feeling bored?

If it's going to be like this, wouldn't it be better to just kill him?

It would be better to just leave them alone or beat them up and throw salt on them, and then make them beg to be killed.

If we keep them alive, they'll just be a burden to the sect and we'll have to take care of them.

However, it was not possible to kill all the prisoners that the other sect had taken the trouble to keep alive.

So what?

\textit{I guess I'll just rest and practice martial arts.}