\chapter{My Prison Experience (13)}

I heard that if you say visitation, it seems like you're going to die.

I know it's not Qing, but it's too suspicious and boring to follow him and say, "Wow, you bastard!"

So, to be a little more persuasive.

As it happens, Qing's hometown has presented a scientific methodology for this.

First stage. Denial.

"Enemies? Enemies? That's ridiculous! I've never left behind any enemies. I sent them all away as companions so they wouldn't be lonely on their way to the afterlife. Where do this enemy come from? You must have misunderstood something. They're calling themselves an enemy of the Apparatus Formation Heavenly King Cha Xiatian, or in short, Cha Xiantian the Annihilator? I can't accept that!"

It's been about six months since the Cha Xiatian came back!

And how was it that Apparatus Formation Heavenly King shortened to the Annihilator?

The corners of the lips of Danlun Zhenren twitched.

Because it's nonsense that pierced through his joke type.

"Hmph, does Karma seems light? Evil deeds inevitably breed resentment. You can never escape the sins you've committed. Just follow along."

But she held on! She did sniffle a little.

The answer of the Danlun Zhenren was not to Qing, but to the prisoners.

Second stage. Anger.

"What kind of bastard are they? I won't let them off the hook. I'll cut off their limbs and bury them in the ground. I'll have to see with my own eyes whether you'll grow a person if you plant a head. You're okay with that life-or-death fight, right?"

"As much as you want. Since you have no dantian and your meridians are severed, it looks like you could be beaten to death by a ten-year-old."

Third stage. Bargaining.

"Umm, Daoist? Could you just tell them that Cha Xiantian was dead? Since she's already dead, they'd still be happy. If you spare my life just this once, I'll be more virtuous. Uh, food, yeah, those food, um. Food is important, but you can cut down just one dish. No, two? Three! Yeah, you can give three bowls of my lunch to that enemy. But if you could give me one dish…"

"Even in this situation, you only care for food."

The voice of the Danlun Zhenren trembled faintly.

In Qing's opinion, he has a blunt way of speaking and a plain personality, but doesn't he have a funny smile?

But in fact, Danlun Zhenren didn't smile much.

Because there were parts that were funnier than others.

It was just that Qing's whining was fitting.

"Okay. Sigh, I guess I'll have to drag you along."

Danlun Zhenren had reached his limit.

If he listened any further, he'd probably burst out laughing.

Danlun Zhenren grabs Qing's arm and pulls it.

Oh, there's still depression and acceptance left!

"No, let me go. What's the matter? Why are you dragging someone along when I said I wouldn't see them? My Lord Taoist? You're lucky my dantian isn't intact. You should not treat this world-renowned master, the King of Apparatus Formation, and the Annihilator of Doors, like this—"

Danlun Zhenren grabbed Qing's wrist and headed out of the Repentance Hall.

Qing was being dragged across the floor while lying down with her hand held.

An urgent voice kept chattering without stopping.

"Hey, Taoist master? Zhenren? Aren't you cool? Handsome? If you're handsome, let me go. If you're ugly, keep going. Wait, why're you keep going? Are you admitting that you're ugly? Do you admit it? Shit, let go, let go for now, don't you understand Zhongyuan language? Okay, wait a minute! Did I leave something behind? Wait a minute, it's really important, my mind is blank, I need to prepare myself mentally, just one ke, no, half ke, no, half of half ke-"

Qing's voice was further and further away, then thud.

The iron gate of the confession hall closed, cutting off Qing's pleas.

Silence fell in Repentance Hall.

It's nice to say that it's like throwing someone to their enemy with their lower abdomen cut off and their limbs and veins severed, but isn't it actually nothing more than an execution?

Although Qing was dragged away in a funny manner, it was like she was being dragged away from the market floor.

However, it was not much different from the reactions of prisoners who have been visited so far.

Because it reminded me of a miserable ending that I had tried not to think about for a while, that I didn't want to think about.

"Who will take care of our food now…"

It seems like they didn't like the atmosphere, so someone tries to make a joke because it's so awkward.

But, once the feelings have subsided, they do not resurface.

It was a request that unintentionally reminded me of the misery in Repentance Hall.

I don't know anyway, and even if I did know, I would have just let it go because it was so annoying.

As soon as Qing closes the double doors of the confession room, she stands up very naturally.

As soon as the door closes, Danlun Zhenren sniffs excitedly and blows his nose.

It's not a strange or weird scene.

Surprisingly, there were quite a few people who laugh like this.

Qing waited until Danlun Jinjin calmed down and then asked.

"So, are we going to have lunch now?"

"Unfortunately, no."

"Oh my. That's really too bad."

In response to Qing's question, Danlun Zhenren bursts into laughter, making him swallow a bowl of snot again.

"The Sect Leader is calling. Either eat and go in, or go in and eat."

So, Qing-i went to Jangmunjeon.

It was a very cold mountain in the middle of winter, and you can feel your breath coming out of it.

However, because it was the Lunar New Year, decorations and lanterns were hung, and the buildings were covered in colorful silk, so even in the cold wave, the faces of the Taoist priests were bright and lively.

Basically, it has a completely different atmosphere from the rather shabby and gloomy Repentance Hall.

Of course, that would be true.

From Repentance Hall, go up the hill for a long time to Jangmunjeon.

The thousand-year-old woman who was fighting the battle welcomed Qing.

"Our Youngesr Sister is here."

"Yes, how have you been, Sect Leader?"

"What could possibly be wrong with being at peace on this auspicious Lunar New Year? Is it cold in Repentance Hall? Should I add another brazier?"

"No. It's not that cold, actually. And it's not like I'm the only one who will benefit from lighting a fire. Each one is very—"

She could barely held back the swearing that was rising to the tip of her throat.

"-They are bad guys."

"Hmm. Okay. How was it spending a day at the Confession Center? Did you have any other thoughts after seeing the sinners?"

"Hmm. Are you saying they're the ones I'm going to kill?"

The sage shakes his head.

"How about this. They are truly worthless. These petty, lowly creatures, these vile, vile creatures, with their meager martial arts skills, have committed all sorts of evil deeds. Now that their martial arts skills have been destroyed and their powers stripped away, they are nothing more than worthless, insignificant, and miserable."

"Even if you say that, I don't feel sorry for them."

The shaman smiles brightly at him.

"I'm not saying we should pity them. No matter how many of them are locked up, how many will truly reflect on their actions and realize they are sinful? Those who in the first place knew and were reluctant to commit sins won't commit sins so grave as to be imprisoned in the Confession Hall."

The thoughts that Qing always kept repeating to herself flowed out of Tian Feizi's mouth.

No matter how severe the punishment, the wicked will never repent for their sins.

They just regret being captured.

If they had known this would happen, they wouldn't have done it.

Well, I didn't know it would be like this until now, so it's been like this all along. Regret was never repentance.

They just want to avoid the great harm they will inflict on themselves, so they won't regret it even if they were imprisoned for a thousand or ten thousand years, not just their entire life.

So the price of sin must be suffering.

After all, punishment could not make a sinner changed their mind, or repent.

So, they must suffer dozens of times more than the evil they have done and the pain they have caused others, and they must die a miserable and horrible death.

A disturbing color spread in Qing's eyes.

That was the moment.

Clap!

The sound of palms hitting each other.

When the palms of the hands, imbued with the pure inner energy of the SangQingmusangdaeshimgyeol. met, a loud, refreshing sound that clear the mind and body awakens Qing's spirit.

"Oh my, how can Youngest Sister's murderous intent be so intense? This is precisely why we built a prison and imprisoned those heinous villains instead of killing them."

"I will listen. What is the reason?"

"Murder, the act of taking a person's life, is the same as killing one's own heart."

Murder, no matter how heinous the criminal, was ultimately an act of killing.

As you become accustomed to killing, you become less and less hesitant about killing people, which means you become reckless.

All those who punish evildoers first carefully examine the before and after.

Is this sin worth paying for with death?

Is there anything that feels unfair?

Are there any circumstances that require consideration, such as coercion or urgent circumstances, etc.

But as the karma of killing piles up, killing the wicked becomes nothing, because the human mind becomes dull to repeated actions.

So, in the past, they were simply killed because they were evil people, and they were likely to neglect human life and justice. In the end, they were killed simply because they were evil people, and even if the victims forgave them, they did not care.

"It's not a sin that Youngest Sister hates the wicked and tries to establish justice in the world by killing them."

Especially when the desire to live was built up through murder, people become more cruel.

This cruelty was truly sinister and treacherous.

Even though they were full of life force and their majesty was like Mount Tai, reaching the sky, they stick out their bellies and act docile like a raised dog in front of their master.

If you hate sin and the wicked, and the hatred for them sinks deep into your heart and seeps into your bones, you cannot be satisfied with simply taking a life.

Death was too easy a punishment, and they become vicious in their desire to pay for their sins with pain.

But as I said before, the human mind becomes dull to what was familiar, so it becomes more and more vicious and seeks to inflict more pain.

This was a vicious cycle that continues endlessly.

Wanting to cause suffering to the wicked was hatred.

Hating others was like giving one's heart to hatred, which was like hurting one's own heart and harming oneself.

The wounds in your heart like that become a pain in your heart.

The pain in his heart turns into hatred, and he tortures the wicked with even more cruel hands in an attempt to heal his own heart.

But how does that heal the heart?

Rather, the wounds in the heart widen further, and the longer the killing continues, the more severe the pain becomes, and the resulting hatred continues to grow.

"Please protect your heart."

The man who said that looked at Qing.

A warm and compassionate gaze, but on the other hand, it seems to see through her inner thoughts.

It was a look that contained the cultivation of an old Taoist priest.

Qing suddenly felt the pattern on the floor very interesting.

Well, she's too ashamed to lift her head.

The reason why Qing slowly slaughters the villain was because he was a son of a bitch who cannot just die, but was that really all?

The slaughter itself was fun.

It's not just fun, it's ecstatic to the point where her whole body's blood vessels were on fire, her mind was dizzy, and her body bounced and convulsed out of control.

But she didn't have the confidence to quit either.

\textit{That touch, um, it's really really good, I don't know how to describe it.}

\textit{But it's also true that it's becoming increasingly cruel.}

\textit{Is it my body's fault or is it because I chose the wrong destiny of Heavenly Killing Star?}

\textit{Or maybe there's already something wrong with me even before I came here.}

\textit{Rather than being hurt, it's becoming more and more exciting.}

\textit{But it's definitely getting duller.}

\textit{At that time, in Luoyang, I fell into a state of ecstasy to the point where I lose consciousness and control of my body just by taking a life.}

\textit{Now, even if I dismantle a body, I don't get that much pleasure, so I'm trying to find more and more novel methods.}

\textit{The Sect Leader's words were correct.}

\textit{This shouldn't be happening.}

\textit{The threshold for satisfaction through slaughter is gradually rising, so isn't this no different from simply going mad?}

Tian Feizi smiled affectionately as he looked at the crown of Qing's head, which has now drooped deeply.

\textit{Was it a good idea to have her stay in Repentance Hall? The child who had previously complained loudly was now bowing her head and reflecting as if she has realized something.}

Of course, it was a reflection that was different from Tian Feizi's thoughts and intentions, but the conclusion was the same.

\textit{Hmm. I should be less cruel, I should exercise some restraint.}