\chapter{My Prison Experience (10)}

Qing's head suddenly turns.

The ten greatest magicians in the world? What was left?

But if it's not the internal energy method, there's no reason to learn evil magic.

Back in the day, when I was a sewer, I might have been excited to collect them all now.

This body was now a true master.

Now, it was Qing who was adept at peeping into the mind.

I know full well how dangerous magic is, and I have plenty of divine powers without it.

But, um, was it okay to just register?

The Ten Greatest Demonic Arts in the World was a kind of insurance.

There were four of the ten greatest magicians in the world that have not been collected yet.

If you fill one here, there were three left.

And since I've been stockpiling my pre-exchanges, I can't guarantee how many points I'll have for the next exchange, but I should be able to exchange at least two.

Maybe even three.

But that doesn't mean you should get hung up on it.

Doesn't that mean that there's still plenty of time to wander the world and that if you keep accumulating good deeds, you'll eventually be able to collect them all?

So, what if I register here?

That's how much time you save.

But Qing just laughs it off.

"The ten greatest magicians in the world? Hey, old man? Do you think the ten greatest magicians in the world were mixed in with the cheap medicines sold by the local herbalist?"

"Newcomer, the Gwangyochui Salganggi was Killer Demon's unique martial art. If the ten greatest demonic arts outside the world were still the same as they were back then, then I am indeed the owner of one of the ten greatest demonic arts."

The opium king in the front room, who had been acting cowardly, suddenly came to his senses and added a commentary.

"Oh. That explanation was helpful. Here, plate."

"Hehe, huh! Other than that, how about the big one next to it? Ohhh, thank you!"

The opium king, who was quite exhausted, was soon in a good mood after eating a piece of meat.

The Opium King was a man who once ran all the opium dens in two provinces and was considered one of the five wealthiest men in the world.

Now, he's just an old man with shining eyes, trying to figure out how to get one more point, and flattering a prisoner who's as young as his granddaughter.

Qing summons the martial arts window and searches for it.

Light-hearted, purple. Internal energy method!

I was just going to register, but then things would change.

What was this, the inner workings method? Just when I need it?

But that doesn't mean you can't hang on.

Qing, hmm.

"Wow, this was truly one of the world's top ten magicians. Hmm, how much would you sell it for if you were one of the world's top ten magicians? You could live off of it until you die, right?"

"Kuuuuuu……. Really, were you feeling better?"

Killer Demon smiles wickedly.

When he was sitting cross-legged, he looked like a normal old man, but the smile that spread across his face was so evil that it seemed like his evil intentions were clearly revealed.

"Are you tempted? Do you even call that a thing? If I said I was selling the ten greatest magicians in the world, the whole world would come dragging gold in a cart… Hmm, no. Now that I think about it, that's not true."

Qing-i shows off her envious expression.

"Now that I see this old man, who were you trying to kill? How can you sell the Ten Greatest Demonic Arts? If you sell it, who'll come with the money? They'll probably come running at you with swords and bloodshot eyes."

"A woman with such incompetence was scheming to escape. It's ridiculous."

Oh, you want to scratch my pride?

I rather like it.

When you want to cry, it's like hitting someone on the cheek, and Qing pretends to fall for it and frowns.

"What? I have plans for everything, don't I? Ha, okay, life's a one-shot deal. Yeah. Go ahead and call me Gugyeol. If I don't see you one day, you'll think I'm selling out the ten greatest magicians in the world and living off my belly."

"Ugh, okay. Come closer and take a look."

Killer Demon approaches the iron bars.

He always sat cross-legged in that spot, so I wondered if he had any problems with his legs, but he walked perfectly fine.

Qing shakes her head at him.

"Just call me from there. What's so great about us that we can just stick together and whisper in each other's ears? Do you think I don't know what's on your mind? What if you bite me?"

"That girl's thoughts were incredibly sinister. Still, she's quite perceptive. I thought it was time to finally taste the blood of a girl."

Killer Demon smiles wickedly.

"Okay. Just call the police."

"Are you talking about now? All those guys have their ears perked up."

"Pharmacists, knife robbers, you guys, speak up."

The pharmacist was in Killer Demon's front room.

The sword robber was a man who collects swords by only cutting down those who own famous swords, and he lives in the room next to Killer Demon.

"Ah …

"Simchaegaehaeng, the five elements, the five aggregates, the tree, Avitabha Buddha……"

Since Qing, who enjoyed almost king-like power with the remaining food, wouldn't the two of them immediately raise their voices and start a disturbance?

"Okay. If you drag it out too long, they'll get hoarse. Sing it louder, louder."

"Kuhaha, what a woman who will live well. Now, I'll sing this song just once, so open your ears and-"

"Once? How can that be? I'll do it until I memorize it all."

Qing laughs fiercely, cutting off the horse's tail.

Killer Demon frowns once, then begins to recite a verse, as if she has no intention of engaging in any further conversation.

"Humanitarian demonstration, killing the enemy during the low-level period…"

The reason people take up a knife was to kill people, so the purpose of studying was solely to kill well.

Killer Demon, who meekly recites the poem with a truly magical introduction.

The flow of internal energy, operation, atmosphere, momentum, and chain were quite detailed, so a clear flow continues.

A unique method of operation in which the true energy first passes through the upper abdomen and then extends to the limbs through the large blood vessels in the middle abdomen.

This requires the opening of the Imdokyang vein.

It means that it was a strong and upward qigong that builds the foundation with the original basic qigong and adds more as you reach a higher level.

But, um. Just hearing this makes me feel a bit…

It's so vicious that I wonder if it's okay to learn it.

It's different from the ignorant Qing of the past.

Now that the foundation of Confucianism, Buddhism, and Taoism itself was solid, the Qing was able to catch up to the level of the masters.

It seems to be a method of filling the upper abdomen with killing intent and turning it around throughout the body, but even without trying it, it's obvious how vicious this martial art is.

It will become cruel and bloodthirsty.

It seems that the stronger the killing intent, the more powerful it becomes. Since the use of the true energy itself evokes the killing intent, the longer the battle goes on, the more the killing intent will rise and the stronger the power will become.

Should we call this a virtuous cycle or a vicious cycle?

Anyway, if we're just talking about power, it definitely deserves to be surrounded by purple borders.

"……If you can kill someone with just your momentum, this was the ultimate martial art."

Then, the corner of her vision started to sparkle.

Surprisingly, the Martial Arts Window notification suddenly light up.

\textit{What is this? Why is it real?}

Qing could not understand.

Didn't you tease him by throwing food at him because you didn't like the way he acted like he was being polite, dignified, and okay when he was the biggest jerk here?

I was planning to let them taste it one by one and then once they got the taste, I would start teasing them in earnest.

So, even as an old man, he must have been quite an annoying opponent.

It's a good thing I'm only annoying, don't you look at me like I'm an enemy just by looking at the dumpling ears in the front room?

That's why I told you to sing it until you memorized it.

Registration was not possible unless the Sutra was intact.

And if you deliberately change and decorate the martial arts formula and recite it over and over again, it will eventually change little by little and the front and back will be different.

Then I thought I would make a big fuss and yell at them, asking why they changed and why they didn't call me properly.

But you're saying that you'll call me by my name without changing a single letter of the martial arts manual?

"Hmm. I think I'll memorize it after about four times."

Since I'll have to use the re-listening function on someone other than the old man, I'll urge Qing to call Gu-gyeol again.

Four times like that.

"Hey, you guys. Stop being so noisy. Hmm. What's your plan, old man? Why does this sounds right? I thought you were going to fake it, but all five time is the same."

Then Killer Demon hissed.

"Would this old man, just fool a woman like you? If you manage to escape, the lineage of the Ten Greatest Demons in the world will continue."

"What, you're always so greedy for disciples?"

"What about disciples? If you escape, I would unleash a vicious, bloodthirsty murderer on the world. How could I not be pleased?"

"Murderer?"

"Ha, I see your level. Isn't this a martial art that blindly creates a murderous spirit?"

It was said that he cooperated obediently without any complaint because it was harmful to the world.

Qing was purely amazed.

Hmm, as expected, the bastard among bastards has a completely different way of thinking.

Killer Demon's smile deepens.

Even though there was no danjeon, there was a thick murderous aura as if black earthworms were being sprayed in all directions.

"Ah, I miss you. I miss you. Do you know the difference between crushing, crushing, and slicing a person's bones? Do you know the feeling of your hands tearing them apart whole, exposing the sharp edges of their flesh? Do you know the sensation of your hands filling up with the sensation of ripping out their internal organs with your bare hands, squeezing them and tearing them apart? Do you know how sweet the screams were when you carve out flesh from their entire body and season it with salt? Do you know the feeling of human fat welling up under your fingernails as you tear away their skin with your hands?"

Then Qing gulped.

Yes, be afraid, Killer Demon's smile grew even more sinister at that moment.

"Wow, what the heck, old man. You know how to kill people?"

Killer Demon's expression suddenly changes and she looks at Qing in a daze.

"What?"

"Shit, after hearing this, I suddenly feel like doing it."

Killer Demon looks into Qing's eyes.

The pupils were dilated and hazy, and the taste was gone.

The most ominous color in the world spreads within it.

A chill runs down Killer Demon's spine.

\textit{This woman, this woman, this woman is a Killing Star, this woman is a Killing Star, this woman is a Killing Star born with a Killing Star.}

Killer Demon, who has already lost his martial arts skills.

But it was an intuition about one's own kind, a certain instinct built up through countless killings.

Qing-eun, the greatest master of the world, was a murderer guaranteed by the two-letter nickname that made the entire Zhongyuan tremble in fear!

If Qing had known, he would have been furious and asked why they were being treated the same, and would have fired a nuclear weapon.

"Of course, that's if you manage to escape. Girl, how do you think that guy you call the Killer Demon got his leg cut off? If you're going to try to escape, do it before the old man gives his order. It'll be fun."

It was a sincere curse that came from a sense of defeat, saying that there would be no escape anyway.

But Qing snorted.

"Just wait and see. Well, a promise is a promise. Yeah, since you're one of the ten greatest magicians in the world, I'll give you a generous reward."

\textit{If I had known this would happen, I would have dug up the old man last.}

You can't mess up collecting martial arts just because of personal likes and dislikes, so you have to treat the first one unconditionally so that others will follow.

Instead of giving her a little something, Killer Demon received a large plate of food that was evenly distributed.

The old man raised his eyebrows at her.

"Tsk, Tsk, I didn't know you could be so kind."

"Huh. I don't like the way this old man act, but you definitely pay the price, right? You're supposed to be generous to your first customer."

"The bones of a thousand-mile horse were worth a thousand gold coins. Yes, that woman was so cunning that a young woman like her must have been driven to this place called Repentance Hall."

This was the story of a thousand gold coins.

In the past, there was a king who gave his servant a thousand gold pieces to buy a thousand-mile horse, but instead of buying a horse, he bought a bone for five hundred gold pieces.

When the king got angry and grabbed his subject by the collar, the subject made an excuse.

'If a rumor spreads that you can buy a bone for only 500 gold, wouldn't all the horse owners in the world rush to see it?'

So the story goes that the king bought three thousand-mile horses and lived happily ever after.

The country's finances might not have been happy.

She threw another three pieces of meat to the drug lord and the knife robber who were shouting and chanting loudly and making a smokescreen.

Then Qing looked down the hallway.

She spoke to the prisoners, who were holding onto the iron bars in the long hallway and intently glanced around to see if there was any food left, while flashing her white teeth.

"So, you see? This is how I roll. Who's going to sell martial arts?"