\chapter{My Prison Experience (9)}

It was so dirty and lethal that I could have just said I didn't buy it.

But the act of monopolization was originally vicious because it was dirty and lethal and could not be helped.

Even without that, the steamed carp was bland at the beginning.

Even with the best stew, it's hard to get rid of the fishy smell of steamed carp, so it's a dish that spreads fragrance. But when I steamed it lightly, it has an earthy smell and was bland, and why were there so many bones?

Among these, there was one guy who sells delicious food.

The quantity was limited, so whoever buys first will own it.

That's why the leftovers business was booming.

This time, there were a lot of dishes on the plate, and I didn't cram them in like I would for lunch, so I still have quite a bit to sell.

Qing, holding such a large plate, smiles sinisterly in front of Salma's brain room at the very end of the room.

"Hmm? Old man, don't you see the fish I dropped earlier? Did you catch it?"

Salma just sat cross-legged and pretended to be deaf, as if she didn't want to hear.

He said that he didn't want to deal with petty criminals like Daemadu, who had a two-letter nickname.

What the heck, were you going to show off and say you're the biggest jerk here?

Qing had already collected some shocking anecdotes about the crimes committed by a vicious criminal thirty years ago, who was known as Salma at lunch.

He committed every crime a human being can commit, including murder, robbery, kidnapping, rape, human trafficking, cannibalism, and fraud.

It was so bad that even the elite seniors of the Wulin Alliance at the time came forward, and the Sadoryeon turned a blind eye and abandoned their own masters.

If things continue like this, the government will probably step in directly, so it was certain that the Sadoryeon has cut off its hand or something.

"Does the old man not want to eat food?"

Qing holds a plate in one hand and chopsticks in the other, rolls a thick, meaty piece of pork rib in chili oil, and then throws it in front of Salma.

"Oh, my hand slipped again? Miss, I was saving it to eat later tonight. Sorry, but you old man, throw it away. I wouldn't pick up a whole hemp seed and eat it like a dog."

Qing giggles and leaves.

Of course, the remaining dishes were sold out.

It was only natural that everyone was offering to buy the dishes, so I ended up leaving half of them to mix in some bland fried rice.

Thanks to that, all that Qing got were dishes that were sparkling clean but somehow felt extremely unclean, countless coals, and seven pairs of the aforementioned utensils.

It was all the coal and artifacts that were in Repentance Hall.

In fact, after watching it for half a day, I realized that it didn't really play with anything.

Well, you must be sick of it already.

Since this was the only thing to play for a long time, the skill gap becomes clear and after playing thousands of rounds, it was natural that interest will decrease.

The reason he kept nagging me while poking me was probably because he was curious when he saw a new face.

But it feels completely different when there were toys in the water and when there aren't.

Things that you would have thrown away without much interest if you could have done them at any time, but once you were actually blocked from doing them, you become incredibly interested in them.

They must have taken away all the entertainment. Won't everyone be incredibly bored tomorrow?

Qing looked at the pile of toys and smiled wickedly.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ding ding ding ding the loud sound of a bell.

Qing was startled and jumps up.

It's an unfamiliar room, an unfamiliar ceiling.

Oh, right. This was Repentance Hall.

The ringing of the bell rings out loud, almost deafening, throughout the interior of the temple.

It was a dark morning, not yet dawn, and the world's pale blue colors were barely visible through the small window.

When Qing peeked through the tent, he could hear people everywhere, and curses like "Ao Shibal" were coming out.

When the bell that had been ringing so mercilessly for a while finally stopped, I felt like I was wide awake, even after a morning nap.

When Qing looked around and wondered why it was so noisy, he realized it was hanging in the corridor inside the Jongmyo Hall.

It looks like it's a structure that makes noise by pulling the strings from the outside.

"Fuck, if only I could sleep in for just one more day, I wouldn't have any more wishes."

There was no one who appears to be just complaining here and there.

It looks like he's still lying on the bed behind the tent.

I wonder if it's been that long.

Ding ding ding ding ding ding The paper glows again and the sharp noise wakes the lying prisoners again.

Wouldn't it be tormenting for a full hour, with the clock resting and the clock ringing four times?

No matter how dull your nerves are, you were no match for the four-time, four-angle, half-hourly bell attack.

Only then does a sigh of relief spread throughout the chapel.

This was what happens every day.

Well, low-salt diets were like that too.

The wake-up bell just rang too.

It seems like they were taking good care of it, but at the same time, I wonder if they were neglecting it, and at the same time, I wonder if there was some kind of extremely persistent malice.

Hmm. The Taoist priests were quite good at it too.

To wake me up like this in the morning without any reason.

Isn't it true that nothing makes you as angry as waking up from sleep?

It was the morning of the second day at Repentance Hall.

"When will breakfast come out?"

"There's no breakfast. Because of that bastard."

"That's right. If I had seen that kid, that bastard, in the martial arts world, I would have beaten him to a pulp."

Prisoners visibly sullen and withered at the thought of not having breakfast.

Each of them, sobbing, slowly disappears back into the tent and onto the bed.

Hmm. No way. Am I missing something?

Should I have left some over yesterday instead of solving everything else?

Morning was the most important element as it was the ritual that announces the start of the day… … .

Of course, if you really want to eat, you can go out and eat.

But doesn't that make you a little suspicious?

Can I just say I'm going to the bathroom?

While Qing was racking his brain over how he could go out and come back on such a natural business,

Suddenly, the door to the confession room opens.

At the sound of the food cart being pulled, prisoners rush out with urgent cries, clutching the bars and their eyes gleaming.

Isn't it the kind of anticipation that comes with the door opening and you coming in?

But the food carts only had covered dishes, not the large, piled-up dishes of yesterday.

"As I said yesterday, you guys won't have breakfast. Just, newbie, how have you been?"

"Yes, I was doing well!"

"Excellent. We should reward them."

"Oh. What the heck, all this stuff. I'll move it."

Qing meets his eyes briefly.

As usual, an indifferent expression, but with a hint of playfulness.

It seems like Danlun Jin-in was really enjoying himself.

Could this really be the purpose of the repentance hall?

You want the disciples to take turns teasing the imprisoned demons?

But breakfast delivery was a joy.

It was an unexpected delivery, so I was doubly happy, as if I had received a surprise gift.

On the one hand, was this okay?

I was trying not to look too suspicious.

"I told you that kid was the worst."

"You always find fault with me and starve me, and then you eat in front of me. Even that bastard was a Taoist. You fucking dog with no mouth."

"Isn't that guy trying to be a jerk and keep doing this until his turn? Wasn't today his shift change? I wonder if I'll ever see that one-eyed bastard again. What the heck, what's with that one-eyed bastard? Did he hit his peak?"

"Even that kid was hitting his peak in the Domun. I thought Seungjil couldn't do it because he's a devil."

Ah. Danlun Zhenren, you were a habitual dharma master.

I thought he was being a bit pushy while giving them food, but it seems he teased the maids like that every now and then.

Making them crippled and locked them up. Waking them up in the morning. Low-salt diet. Neglect. The inmates' disposition to swear.

In summary, it was the moment when the speculation that the very reason for the existence of the Repentance Hall was to keep the Madu alive and play with them for a long time turned into certainty.

Anyway, I'm fine.

Then, morning business will be good too.

Inside the restaurant, the sound of people eating continues, and the smell of cooking fills the air, making people gulp.

After waiting so patiently, the long-awaited voice finally came.

"Hey, who wants to buy some food today? I bet you were all thinking about what to sell last night."

"Me, me!" "New girl! It's me! It's me!"

Madhus, sending you their enthusiastic support once again,

As Qing said, the madu had been worrying all night about what to sell.

"Well, there's plenty of food. Now, who wants to start? Yeah, it's in the next room. Doksalma, what do you want?"

"Well, there's a secret recipe for poison. Would you like to buy it?"

"Poison? Is that stronger than blood poison?"

"Blood poison? What kind of poison was it?"

Hmm? Wasn't it a fairly famous poison?

I thought it was somewhat notorious since even the Xuega Sanghoe would understand it.

"Don't you know about blood poison? The blood poison of the deadly disease."

"Sasa? Who was that? Is that the Madou who's out there right now?"

Ah. This.

It's not that Blood Poison isn't famous, it's just a generational difference.

Because it was a village where news from the outside world was blocked, they do not even know about the masterpieces of Sasaui, who was quite famous.

"Ah. You don't know about Sasa. It's a poison that causes pain as if your entire body was being torn apart by a swarm of ants. I don't know what it is, but it must be stronger than that, right?"

"Well, I thought it was just a way to kill time anyway."

Qing snorted at him.

"You guys, you seem to be mistaken. I have no intention of living here with you. And what will you do if you leave in this state? With your dantian shattered and your meridians severed, what kind of work will you do? Shouldn't I be out there and selling something?"

"What about escape? Wake up, you bitch. Do you think the flying and crawling demons have been lying around comfortably all this time?"

"You'll see, right? Well, anyway. So I need to find my own way. You're going to be stuck here anyway, and honestly, I didn't give you any food in a bad way, right?"

"hmm."

It's not the first time a newbie has talked about jailbreaking.

I already remember all the madrasas coming in for the first time and declaring that I would definitely leave.

So I didn't bother to say anything about whether that would work or not.

Of course, that's why I'm just throwing the Qingdao.

Surely there isn't a single person here who hasn't attempted to escape?

If you think it won't work out anyway, I think you should go out and sell it if you can, and I think you'll throw out sensitive information.

So, Qing comes out of the iron bars again and examines the information presented one by one.

Actually, I'm not interested, but if I accept anything, I don't think I'll ever hear about the internal energy method even if I sell leftovers all day.

Qing looks at the last room, Salma.

The old man still sits cross-legged with dignity.

But Qing didn't miss the tiny stains on the corners of her mouth, the yellow traces of chili oil she had rubbed off.

The moment the original chili oil meets pork fat, it becomes a vicious stain that was difficult to remove even if you lather it well and wash it off.

Since they threw pork ribs at you, it wouldn't be easy to not get them smeared somewhere, no matter how cleanly you eat them.

This old man ended up picking it up and eating it.

Then, across the street, the opium dealer pleaded with his characteristically flattering voice.

"Newcomer! How about this? It's a recipe for the Paradise Incense!"

"Paradise? Are you smoking opium?"

"That's right. Wouldn't this be a trip to paradise if you could just get this one? Aren't you curious?"

"Um, do you happen to know Bingdu?"

"Ice? What was that?"

"These days, they don't do the old-fashioned things like melting it over a fire and smoking it. If it smells, everyone will notice, so it's crazy. They grind it into powder and suck it up through their nose or stick it to the roof of their mouth. How many decades ago was that trendy thing called 'Gukrakseonhyang'?"

Of course, drugs had not yet developed to that extent in Zhongyuan.

But I'll go out and find out.

Even if you just throw it away, it's like that.

"Wow, they're already made so much progress, rookie? Could you elaborate on that a little more?"

"I haven't tried it myself, so I don't know the details. But I heard it's really fun."

The opium addict fell into his lap.

He looked very shocked.

I wonder if it's something that should be that shocking.

"No, what, there's nothing but stale stuff here? Who was the last one to come in here?"

"The adulterer last came in there eleven years ago."

"Oh, that big killer. There's no such thing as a free lunch, so I'll give you a piece of meat. But, shit, the latest information is from eleven years ago? You guys are really no help at all."

Qing let out a deep sigh.

\textit{But still, I feel quite anxious.}

\textit{If I do this, I wonder if someone would ever take a bait. Please, just catch one. If I just get one person to confess, the rest will all confess like crazy.}

That was when.

A voice that was completely unexpected came to Qing's ear.

"You're a funny woman. Escaping from prison? If you're so inclined, go for it. But would you sell out even Ten Greatest Demonic Art in the world?"

Huh. The Ten Greatest Demonic Art in the world? Here?