\chapter{My Prison Experience (6)}

The meal at Repentance Hall was better than Qing had expected.

A whole chicken and a mountain of dumplings?

Even though it's a special dish, does this make sense?

For reference, dumplings were one of the New Year's foods in Zhongyuan. The pronunciation of dumplings in Gangse-gyoja, which means letting go of the old year and welcoming the new year, was the same as the food, dumplings.

No, what was it?

I was on the street and had nothing to eat, so I just picked up whatever I could find and ate it.

Aren't these bastards the scum of the earth who were captured and brought to Repentance Hall?

I must have been doing well even back when I was living a beggar's life, eating three meals a day and patting my stomach.

Wouldn't it be better to just use the money we save for these kids to help the starving people on the streets?

When I think about it that way, I just don't understand.

Why did you keep him alive and keep him so clean when you could have just killed him?

At first, I thought maybe he even took care of his beard since there weren't any bearded men, but now I see that it's probably just because he's a eunuch.

Even so, the fact that there was no particular bad smell or anything shows that the cleanliness inside the Repentance Hall was well maintained.

Why on earth did the Great Master Jang Moon Jin insist on experiencing the Repentance Hall experience?

If you feel stuffy, you can come out, and if you go to the trouble of providing a high-quality bed (of course, this must have been done by a disciple of Kunlun), and if you were even allowed to sleep in the guest room at night, isn't it embarrassing to even call it an experience?

I could understand if the treatment of this evil bastard had been harsh and cruel.

It's embarrassing and hurtful, and I don't understand the emotional part at all, but anyway, it's not like I realized that instead of brutally killing them and putting them on display, I should just throw them in a brain prison and make them suffer for a long time.

But I'm sure Zhenren has his own thoughts.

Qing relieves this frustration through frenzied eating.

The poor dishes were chewed, crushed, and shattered by the pure white teeth of the blue dragon and then gulped down.

Well, it still tastes good.

He said he would let me eat as much food as I wanted even if I entered Repentance Hall.

But, um. You said to eat as much as you want.

Qing looks down at the cooking utensils.

Five dishes, five large bowls, and five servings.

And yet, the remaining amount was enough to be evenly distributed.

What the heck was this? What on earth do you think people are?

How can a human being eat all of this… … .

Shock! I declare that I can't eat the amount of Ximen-Qing!

Shocking! Seo Moon-Qing, the owner of an inhumane diet, redefines human standards!

The Kunlun sect Taoist priests, having seen Qing's appetite, generously provided him with more than he needed.

The Zhongyuan have an underdeveloped food culture that always ends up leaving food behind and creating food waste!

But I can't possibly eat this much. It's humanly impossible.

Qing was a person who was careful not to leave any food behind.

It's a practical attitude that doesn't seem like a Zhongyuan, but it's also because of the spiritual roots and the limitations attached to food.

So I ate until I was almost full, and then I decided that this wasn't going to work.

Even though it was a denim that stretched out the stomach and belly skin as much as possible, there was no technology that could compress it to the point of ignoring physical space.

The ship was already on the verge of bursting.

Food that clatters all the way up to the chin.

So, Qing sat on the floor with his palms behind him and stroked his stomach.

Still, my gaze was on the food.

It's a bit weird to leave behind food that was made for you.

I'll leave it alone and eat it slowly when it cools down a bit.

It wasn't something that a person with a belly as big as a mountain would usually think of doing.

It's because I have a grudge against food, so I guess you could say it's an unavoidable foolishness.

And only then did I notice the prisoners in front, left and right, looking at me as if they were dumbfounded.

Hmm. I was so focused on eating that I didn't even notice.

Since they were guys without even a single danjeon, well, I guess I need to reflect on this a bit.

I guess I've become so used to living like a true master that I don't care about the common people at all.

Well, since he had already achieved a high level of self-confidence, shouldn't he be afraid that his clothes would be torn if the civilians attacked him with knives?

Because it has a monstrous body that can drink poison from a bowl without any problems.

So it seems that they considered those without martial arts skills to be completely harmless.

Moreover, it was taken for granted that onlookers gather during the meal.

"What? Is this your first time seeing someone eat?"

"Are you even raising a beggar in your stomach? Is that how it fits in?"

"Huh. Mr. Nam. Why?"

"No, that. I was just wondering if you ate it all."

The prisoners' eyes wander between the food left behind by Qing and his swollen belly.

The eyes looking at the food were earnest, and the eyes looking at the blue boat were like those of an individual who had become infinitely small before the wondrous mystery of the universe.

Since I can't take my eyes off of either of them, I have no choice but to keep rolling my eyes back and forth.

Qing sits with his chin on his hand behind his back and declares to those busy eyes.

"If you like free food, you'll end up like that dumpling ear? For three nyang, you'll have a dantian, a meridian, testicles, and two arms. That's a miracle man! That's why you're no longer a man!"

A loud burst of laughter erupted from the distant brain, and the expression on the man with the dumpling ears suddenly turned rotten.

Qingdo giggles, his stomach tightens as he laughs, showing signs of reflux, so he quickly suppresses his laughter and speaks with a serious expression.

"Jessiyo. How much research have you done?"

The Qing poisoned Zhongyuan.

The primitive people of an uncivilized society still dare not come to their senses and just open their mouths in the face of the cutting-edge and most brutal commercial techniques that were still hundreds of years ahead of their time.

Besides, you have to have something to offer in the first place, whether you offer it or not.

Of the few pleasures one can experience while living in Repentance Hall, the one that takes up the largest portion was food.

So, didn't the dumpling-eared man make a very big decision to escape together by offering a special meal in a very serious manner?

But what on earth would the prisoners have to offer when faced with a dish more precious than a special meal (leftovers, scraps)?

"Well, I don't have anything to give you except coal. Would you like this?"

"Carbon? What was carbon?"

"Ah. You're new, so you don't know. This was a coal mine. You'll need this if you want to live in Repentance Hall. It'll at least help alleviate your boredom."

In the room on the right, a man with a crooked nose holds out something dark and tacky.

It's something that looks like a go stone, has holes on one side, and isn't that heavy.

Charcoal? A bouncing stone?

It was said that it was made by rubbing the bones of cows and pigs well.

They play a game where they bounce stones to hit each other's bullets and send them out of the line.

That is, it was a secret.

Qing looked at the square line drawn between the two rooms under the iron bars on the left and right with a sour expression.

"Okay. Anything else?"

"Or maybe it's something like the above…"

"Huh? Remember? Remember that too?"

The above was the prototype of a folk game called Janggi in the hometown of Qing. The pieces were the same, but the rules were more complex and have more restrictions.

"Are you saying that you even included a reminder to not be bored in Repentance Hall?"

Even so, it wasn't that far.

When I received the soldier's equipment and examined it, I saw that it was made of either pig or cow bones with letters scratched on them.

This was completely handmade.

What a worthless handmade product.

"Even the idiots know this, but they turn a blind eye. If you don't do it openly, no one will say anything."

"hmm."

I think I know why.

When people were bored, they go crazy and you never know what they might do.

If you just pretend not to know and let them have fun, they won't do anything else, right?

"Okay. Let's hear what you have to say. How did you end up here? Are you afraid of the consequences and came here to annihilate people?"

"Ahem, don't compare me to that ignorant bastard Wooga. He's the infamous backstabber."

The neighbor on the right, Ppoon-ko, glances at Qing. Dumpling Ears and Baemyeonsal-gwi look at Qing as if expecting something.

Even if you look at it that way, you don't know, and it's weird to pretend to know a guy who's got three nyang of silver and a hemp head.

What kind of a hemp head was he who was so upset and immediately tells you?

I really need to remove the peppers, no, I already removed them.

Mandugui looked obviously disappointed.

The pouty nose looks like it knows something.

"It seems like the newbie was still young."

"What? You want me to treat you like an elder?"

"There's no need for that. It'll come naturally after ten or twenty years of seeing each other. Anyway, if that guy over there weren't here, he'd have been captured by Shaolin monks. If he escaped to the Qinghai Sea, he probably thought the Kunlun Sect was easy."

"Hmm. But Shaolin can be scary, right? Hmm? After all, weren't they all captured by the Kunlun sect?"

"At least not me. Wouldn't it be foolish to flee to a land occupied by the Malkos, who claim to possess the most divine powers in the world?"

There were sighs of "Ahh" here and there.

These kids were pretending not to hear but they're listening intently.

"I was held captive by the communist faction, but when the Tangchang Massacre broke out, there was no place to stay in the communist faction's preparation room, so I came here."

"So how did you end up in the communist group?"

"I can't say I'm innocent, but I haven't committed a crime so grave that I deserve to be locked up like this for the rest of my life. However, as you know, those Gonghap Malkos were the ones who cause trouble."

"Ah. So you feel wronged too?"

Qing's eyebrows twitched.

Isn't this an unfair evil deed?

"Well, aren't more than half of the people imprisoned here notorious villains? Compared to them, I just made a minor mistake."

"What's the mistake? That guy's the one who mixed poison with a medicinal herb and then sold the antidote, pretending to be a god."

If there were no patients, just make them!

Is this what a creative economy was like?

Qing's eyes narrowed.

At that expression, Ppoonko quickly made an excuse.

"Don't look at me like that. Even if it was poison, it wasn't lethal, and even without taking the antidote pill, your life wouldn't be in danger."

Qing's eyes narrow further.

Even if I don't take the antidote, my life will be safe?

Anyone who defends themselves always says things that were favorable to me.

As long as your life was safe, I hope it's not in danger.

It means that one or more places become disabled.

As the corners of Qing's eyes tremble, a commentary was added from the left room.

"Of course, he caused a big accident while mixing poisonous medicine like that, so the fact that four hundred people died in the Cheonsuhyeolsa was that bastard's achievement."

"That was a mistake. It was just something nasty that got into it back then. Even now, I can't quite figure out what the problem was. I never put anything that toxic in it in the first place—"

"It's only a matter of time, anyway. Did you think he'd never make a single mistake while doing that? Who knows. If you dig into his other crimes, he might have been responsible for the massacre, among other things."

I am once again amazed by the insight of the Kunlun School.

This bastard was also a bastard, really.

"Well, I've got enough, so give me a bowl. I'd like to say there's no soup, but I'll have to pay for what I've heard."

Qing distributes food and meals little by little through the bars of the window.

"Well, if you could give me one more big piece… Oh, were you curious about the other guys' stories? As far as I know—"

"Shut up, you idiot! Why were you trying to sell out someone else's business?"

In the left room, an ugly man urgently cuts off the stone-thrower's words.

His face was ugly, but his voice was deep and heavy with a deep, deep tone. Is he a voice actor?

Like the primitive ancient voice actors, the benshis who only provide voices in mask plays or puppet shows.

"How did you get caught?"

"It's all because of dirty jealousy. He can't even keep his own wife safe."

"Huh? An affair? With that face?"

Qing looked at the ugly man in the left room, his unusually broad nose as wide as the ocean and his crooked teeth.

"They say a quack was a young woman, and that's exactly right. Young women think their looks were the best. But what matters most was their heart, right?"

"That kid was acting up again."

"What was the mind of a man trapped in the prison?"

He was met with fierce criticism.

Thanks to that, I was able to roughly figure out the charges by combining it with Chunam's testimony.

Surprisingly, he was a serial cheater!

With that face!

Then, Chunam puffs out his chest in a proud manner and starts to show off.

"Do you think the ladies from well-to-do families would even look at a man's face anyway? There's no such thing as a man from a well-to-do family who isn't handsome. So, I've seen enough handsome faces already."

Rather, if an ugly guy comes at me, I'm curious and want to hear what he has to say.

After that, the passionate love that her husband cannot give her, and the fantastical art of infidelity combine to make her just a prisoner of love.

Rather, they think that because I'm ugly, people will only look at me or something.

Serial cheating was really petty and funny.

Is an affair something that was done alone?

The other side also agreed, so they played with fire together, but it was too cruel to be locked up in the repentance room because they became such a cripple.

"Right? Those guys who can't even take care of their own wife were doing so well that it's so damned good that I'm in this mess now."

In the end, he said he was being treated unfairly.

The serial adulterer only bothered with the wives of noble families, so the noble husbands conspired to throw him into this charade.

It might have been unfair if there had been no commentary from other prisoners.

"I told you, that bastard was a total piece of shit. He stole the checkbook and all the family assets that were left on the battlefield, so he ran off with a few of the family's most important assets. If his wife were to become a cripple and wallow in cheap prostitution, it would be enough to make men roll their eyes."

In the end, he stole all the family's belongings, saying he was going to run away with his precious wife, and then he cut off her tongue, severed her veins, and sold her into prostitution.

Just as the men of noble families were generally handsome, aren't the wives of noble families also bound to be beautiful?

I guess he would have made a lot of money selling it.

Thanks to that, Qing had to think seriously.

Shouldn't this kid just be given the opportunity to have his skin peeled off and then fed a salty, rich soup instead of eating it?

I think even Master would praise this kid for doing well.