\chapter{My Prison Experience (12)}

The spirit of the Qing was awakened.

Originally, it was a time when I had to lie down for half an hour as a side effect of the brain-scratching learning method.

But suddenly, a severe pain surged into my lower abdomen, as if boiling iron had filled my abdomen.

As soon as I learned the Gwangyochusalganggi, my dantian started to hurt, and the pain was so bad, I'm dying.

It felt like I had a full-blown stomachache, as if my stomach was being ripped apart, and in an instant, cold sweat poured down my face and I automatically let out a groan.

What's wrong, my wound? Did I get sick from learning magic?

Ugh, save me, what was this, ugh.

The killer laughs heartily.

It was a murderous laugh that somehow felt like it had to be written in the Western characters.

At that moment, there were some little guys blocking the way of the Gwangsalmagi.

The Great Tranquility True Qi and Zhu Heart Cleansing Mirror True Qi were the two Divine Arts responsible for Qing's mental health.

The most vicious Demonic Art that infects the upper body with murderous intent and leads the owner to death.

And two legendary Divine Arts that purify the upper body and protect the mind.

Two opposing energies faced each other, unable to tolerate each other and therefore incompatible.

The three True Qis locked eyes, and a tense atmosphere bloomed like a black line.

And finally!

As if they had made a promise, the three True Qis all rushed towards the opponent, pounding on the floor.

Thump thump thump! Pat thump thump!

A truly heart-pounding battle!

But delicious food can be harmful to the body.

The pleasure one gets from killing another was a great pleasure that cannot be compared to the act of quietly meditating and studying the words of the wise.

The latter was boring and tedious to begin with, and doesn't provide even the slightest bit of enjoyment.

So, despite this fight, both of the gods get hit and get bruised and injured.

This was the fear of Demonic Art.

Because humans were always vulnerable to the temptation of magic, they were creatures who cannot help but be shaken.

At last, the moment when the madman opens his mouth wide and was about to bite the king!

A splendid double drop kick by a True Qi in a monk's attire, boldly exposing one breast, flew at the speed of a typhoon and hit the side of the swordsman.

And next to it was the Mansangyeo Ilgi, who was dressed in an equally daring outfit, but was covered only with jewels, making her look very desirable.

And then there's the True Qi carried by a dragon and an elephant, who were screaming "Poo-Poo-Poo" and "Kururururur" in anger.

It was the participation of the three sisters of the Heavenly Kings.

'You bastards!' The Demonic Qis tried to rush in, but Blissful Maiden True Qi blocked their way.

It was an obscene sight, with only a piece of cloth and ornaments covering the body, but the expression was quite vicious, and the eyes were glaring with joy.

The Demonic Qis stopped with a squeak.

The memories of all the beating they've had so far were slowly starting to come back, so they couln't just rush in.

The Ice Art True Qis, hugging each other around the iceberg, were crunching on popcorn that came out from somewhere and having a front seat spectacle.

The fight between the purple martial artists was five to one!

A truly heartbreaking fight!

Even though she was a madman, she was no match for the five Divine Arts, so she ended up covering her head, crouching down, and bowing deeply to the ground to avoid being beaten in the face.

The sound of dust being cleared away continued for a long time.

It was a time when the tiny pupils of the Gwangsalmagi's eyes turned into the letter 乂 and blood flowed out of her nose.

Suddenly, the bodies of the five True Qis floated up, and the sound of the Moon Maiden True Qi's footsteps echoed between them.

Well, the Moon Maiden True Qi was the very essence of moderation. Because it didn't not allow the destruction or disappearance of True Qi.

The Divine Arts True Qi smacked their lips with regretful expressions.

They thought it shouldn't end just like that.

However, the Demonic Qis were aggrieved as well.

'If you're going to stop it, you should have stopped it a long time ago.'

'What was the purpose of watching someone get beaten to the point of becoming a rice cake and only then stopping them?'

'That bitch, she's absolutely not being neutral'.

Then suddenly there was an unpleasant laugh.

Keuhihihi, keukhi. The Heavenly Demon True Qi will be more hilarious than usual and will probably be giggling.

There was a murderous glimmer in the eyes of the magicians.

In sociological terms, this phenomenon could be described as being very hawkish.

Qing's distorted expression, lying on the bed and sweating profusely, suddenly becomes calm.

"Hmm?"

Because the sudden sharp pain suddenly disappeared with a sudden relief.

What? Again all of a sudden?

As Qing blinked, wondering what on earth was going on, the amount of Pacheon Magic that could be used increased to the size of a booger.

When you learn a new technique, your available capacity increases a little, but I don't know the principle, but it's like this.

Anyway.

After finishing the morning business, quite some time must have passed already.

Of course, business in the morning wasn't smooth.

For example, that knife robber.

"Hey, the instructions you gave me earlier were different. This guy's a total rip-off. You said you were going down the non-floating acupuncture needle earlier, but why were you turning to the right this time?"

"Oh, did I do that?"

No, it wasn't like that.

But I know you lied to me.

There was no news about the martial arts window, and since it couldn't be registered without a proper spell, I just did a quick stab.

But the swordsman who had called the swordsman was very embarrassed.

Anyway, I think he's a son of a bitch who got caught in a cripple's den in Repentance Hall. He's really a scammer, a scammer.

It wasn't something that the con artist, the worst of the con artists, would do without hesitation if she were a villain.

"You didn't call me correctly? Try again from the beginning. Isn't this a total rip-off? I don't deal with rip-offs."

Qing puts a stop sign on him.

Of course, even if you were a swindler, you don't do business with swindlers, so what Qing said could be said contrary to what you might think.

It's just empty talk, but you don't know what's wrong with it.

How could the prisoners in the prison know?

In this way, the sword robber was stripped of his inner strength.

On the other hand.

There were even some who were learning it wrong.

Dumpling ears were one of them.

"Is that right? Are you sure?"

"Fuck, I said it right, bitch, you're gonna get blisters in your mouth, how many times do I have to tell you?"

I called twenty times, but there was no reply.

However, in Qing's opinion, this kid with dumpling ears was clearly uneducated from his words and actions.

In other words, he was a man who didn't have the talent to deceive others by writing such letters.

Only then does Qing realize one unfortunate truth about the martial arts world.

Learning complete martial arts was not as easy as you might think.

Moreover, if the martial arts master carelessly touches something thinking it would be better this way, even if it seems to be effective right away, in most cases, there will be side effects in the long run.

So, didn't your master tell you not to just pick up and swallow any knots just because your dantian was special?

"You have to be able to trust me. Now, hand me the bowl."

"You bitch, why were you rolling your eyes like that?"

Well, that's pitiful.

Since I believe that the flawed martial arts were real, isn't one of the reasons I'm locked up here with my limbs crippled and a sledgehammer because of that side effect?

But somehow, the eyes were filled with pity, and that is, pitiful eyes, and Dumpling Ears bristled.

Anyway, since I told you what I know, you should give me food as promised.

In addition to that?

What the heck was a little kid that only knows a little about?

"It feels like something was cut off? What about the latter part?"

"Unfortunately, my chance ends here. The back of the book was missing. Ah, if only I had a complete copy of the book, I could have become a master who could reach the world."

If you search by martial arts name, it has a golden border. If the martial arts were complete, he could have become a truly famous master.

Even so, aren't people just like that, like a bunch of idiots?

Even if he had a perfect lifespan, that son of a bitch wouldn't have become a sage.

It makes a difference whether you come to Repentance Hall early or late.

"This isn't it. How can you sell half-baked martial arts? I don't need this kind of thing."

"No, even if you don't know the latter half, it's a martial art that has reached the peak of its power, so what else can't it sell?"

"I don't know the second half, so I guess it's only the most extreme part. Anyway, you're out. You can't eat the food."

"No! Where's that!? Look! And you're saying it's only a super climax review? Hey, you punk, where the hell were you to say all you did was watch a super climax review?"

"Yeah. I'm Jaeyeon-gyeong. You're a total nerd."

"What?"

"Oh, dear. Even if I lost my dantian, do I really need to talk to someone like that? Oh, I'm wasting my time. You sloppy brat. So, between being a eunuch and being a eunuch and being trapped, I chose the latter."

"What!? Hey! You bitch!"

So the morning business was over.

And while lying on the bed, I registered the temporary ones and raised all the blue ones that didn't cost much in training points to the maximum level of ten stars.

This was the moment after I drooled all over my brain, groaned, and then suddenly got better.

Qing checks the total amount of internal energy.

Since I originally had a lot of internal energy, it didn't increase much even after a lot of mind techniques were added.

At this rate, when will I ever be able to raise this little bit of internal energy to something beyond reality?

At least the full capacity of the Heavenly Demon True Qi, that is, the level of the mental parasite, so I think that would be a life and death situation.

Should I also stop by Repentance Hall while looking at the cliff?

After a brief period of idle thoughts, since there was nothing else to do, he went back to the primitive ancient training method of the uncivilized warriors, meditation, and developed the Mansangyeoilsingong.

By the way, cutting-edge unmanned vehicles don't meditate.

Wouldn't it be great to kill the bad guys and earn training points to level up?

If you only meditate, when will you ever develop your inner strength?

Of course, the primitive cultivation method, which continues to grow and gain speed without limit, will become much superior when it reaches the present.

In the first place, anyone can go to Hyeon-gyeong.

Since there was nothing else to do, Qing, who had become more sincere, continued to practice dantian breathing on the bed.

And how much time passed?

A fragrant smell suddenly rises.

And the sound of a food cart rolling.

The door to the chamhoe-dong was a wooden door with iron plates. It opened very smoothly and without making a sound, so I don't know who made it.

Ah. Lunch! It's lunch!

Qing was so excited that he lifts the tent and runs out.

"Today's lunch was perilla seed porridge and boiled pork."

The names of dishes in Zhongyuan were very friendly, usually consisting of the recipe plus ingredients.

The water was boiled. The meat was pork.

That is, meat!

Looking at the way Qing serves food, it seems like she'll be filling up the delicious perilla seed porridge with tender, well-boiled pork.

But, they don't give you any sauce to eat with it.

I feel it again, but it was secretly malicious.

Perilla seed porridge was of course rich and delicious, but isn't it just a bit bland?

They even gave me boiled pork without even giving me salt.

however.

No plates?

What about my food? What about my cooking?

As the blue pupils caused an earthquake, the single-wheeled Zhenren passed the blue brain jade and circled all the way to the end before standing in front.

And then he said.

"It's a visitation."

The atmosphere inside the repentance hall suddenly became cold.

There were sighs of 'Fuck' coming from the other side.

What? Dumpling ears? What the heck, a sigh? Are you feeling any resentment?

A muttering sound followed.

-If that girl die, who will bring the food now?

Well then, I guess I was just focused on cooking.

By the way. Am I going to die?

Wasn't the punishment for repentance permanent isolation, life imprisonment, or life imprisonment?

"What is it? What is this atmosphere? Master, what is this visitation?"

Then Danlun answered kindly.

"It's just it says. Someone wants to see you. But who else but their enemies would want to see the vicious demon? We don't encourage revenge. But we don't discourage it either."

\textit{Ah. So that's the setup.}

\textit{Well, even if we assume that there were fourteen prison cells in Repentance Hall, and each of the Orthodox sects operated one Repentance Hall, there were still a little over a hundred prison cells.}

\textit{The Zhongyuan was so vast and the number of bastards was countless, how could they possibly handle it with just a little over a hundred cells?}

\textit{It seems like they gave it to their enemies when they ask for it.}

That didn't mean there's any reason for Qing to be afraid.

She just understood.

Somehow there was no extra food.

\textit{I wondered if the kids had called me to have lunch together since I hadn't come out of Repentance Hall.}

\textit{But it's a bit boring to just follow along.}

Qing's eyes sparkled with mischief.