\chapter{My Prison Experience (14)}

"The repentance was a means to prevent the disciples' hearts from being hurt."

No matter how much you confine it, evil does not change.

However, if one were to kill an extremely evil person, the one who kills him would have to take the risk of killing him.

But what if you abandon martial arts and lock yourself up?

Only the evildoers who were harmful to the world were imprisoned and isolated, which was beneficial to the world.

Since it doesn't cut down, no one has to accumulate karma.

If there was someone who wants to take his life, I will give it to him, and if he wants to take proper revenge, I will not necessarily stop him.

"Our Kunlun is not so poor that we can't even feed a few of those Demonic Adepts. But even if we were poor, we wouldn't close the Repentance Hall. A disciple of Kunlun who suffers a broken heart is a loss worth more than a thousand pieces of gold. So, even if maintaining the Repentance Hall costs a great deal of money, how could we say it's expensive?"

"Ah…"

"It is also proof that evil is not something grand, and that the honor built up through evil deeds is ultimately an illusion that does not exist."

Look at those dirty, shabby heads.

They were people who had no fear when they were in the world of martial arts, so they lived in luxury, enjoying a good home, good food, and living in luxury, thinking that it was the most precious thing in the world.

But what about them now?

A bunch of little people who pick up fallen meat and eat it, and grumble about how some people's chicken legs were plump and some people's chicke legs have bones showing.

They fought with their lives on the line in a game of bouncing off a few pig bone pellets to get a few more.

They were truly insignificant and crippled.

"That is why the disciples, while caring for the repentance hall, can confirm that the true nature of the great evils are also an infinitely selfish and pitiful individuals."

Those who were so evil that their names were known throughout the world.

But what was the reality?

Those hearts that were left after losing their strength were just worthless and shabby.

A person who was just greedy and lacks self-control.

"Even if it was the Great Demon, it was not some evil that the world has forced upon us, but rather a series of indulgent choices driven by greed. The wealth and honor gained through evil deeds do not elevate a person's essential dignity."

In this way, the disciples came to realize that the fruits of greed and evil deeds were illusions that will be taken away and disappeared when they lose their power.

There were values ​​in the world that were not illusions.

There was value that remains even if power was lost.

Cultivation for personal perfection.

A friendship built through fellowship in the heart, not through the exchange of goods.

Dear companions and family.

After returning, etc., because of the favors given.

"Did you see the Demonic Adept trapped at the very end? He was the Demonic Adept of the Demonic Adept, the one who shook Zhongyuan in the past, known as the Killer Demon. He was also a demon who mastered one of the Ten Greatest Demonic Arts in the world."

"You mean that old man who pretends to be polite?"

"Yes. At some point, he started acting polite. Perhaps he realized the purpose of the Repentance Hall and decided to exploit the loophole. But does that mean the dirty deeds he committed will be forgotten?"

"So then?"

"Didn't he get so upset if the amount of food given was even slightly less or if there was not enough meat, since he was a senior Demonic Adept?"

But what harm could a man who had lost his martial arts and was locked up could do?

So the solution he came up with was to throw his own feces.

"Ugh, that old man?"

"Isn't he the ugliest of filthy creatures? That's why we fed him only water and barley flour for every meal, and told him he would continue to eat that until he knelt and apologized. He lasted about a month, I think?"

Water and barley flour may seem harsh, but that was the typical diet of the Jjampa, the Jang tribe of Qinghae.

"Did he get on his knees and apologized?"

"He pretended to fall down and knelt down, and mumbled, ‘I'm sorry,' so I don't know if that can be called an apology."

It would have been better if it had been done properly.

Just get on your knees and apologize like an adult. 'It was an immature thing on my part, and I apologize for the dirty prank I played earlier.'

But isn't food the only thing you can enjoy in the life of a monk and not something that people eat fatally?

If it had been like that, there might have been some respect left for the prisoners to treat Killer Demon as a senior.

But the guy who was holding the weight of the situation with such dignity and dignity gave in so hastily and shamefully.

From that moment on, he just became a helpless old bastard who just held onto past glory.

Since then, the prisoners in Repentance Hall have changed the way they call him. The seven-letter "Gwangsalma-gun Elder" has been innovatively shortened to three letters: "Ya" and "Killer Demon."

This was the way of the wicked and why they received their karma back.

Since they were unwilling to accept even the smallest loss right in front of them, they end up resorting to tricks somehow.

Then it comes back as an even bigger loss.

"Before telling Youngest Sister about the Repentance Hall, I wanted her to see and hear for herself the true nature of those vile, evil people. What do you think of it now that you've been there? Do you still believe that evil people should simply be eliminated and that the Repentance is unnecessary?"

"No. I think I know what you mean. They're definitely people with no pride or anything left."

Tian Feizin smiled kindly.

"Okay, that's enough. If you feel there's no need to stay any longer, you can stop. However, I'd like to see it through to the end. Seeing things without knowingis different from seeing things with knowledge. I hope you'll once again see the ugliness of the wicked and take the lesson to heart."

"Even if that's not the case, if Martial Brother ordered me to do it in the first place and I left midway, even if he allows it, how can that be a good thing?"

"Haha, Youngest Sister knows how to save this Martial Brother's face."

He was a commoner who was properly treated by the old man murderer.

No matter what Qing says, it looks cute, so you could say that it's a serious level of aegyo addiction.

It's not the fault of the poor.

Originally, the elder of the Venerable Master was an extremely difficult elder, so how could disciples of the same age as him approach the Grand Master, who was like a teacher to his teacher, or even a teacher to his teacher's teacher?

So, regardless of their age, old masters were inherently lonely beings.

The Sega clans, which were blood relatives, were a little less so, but the elders of the sect were lonely and bored every day.

So, they were all poor old people who can never escape the Qing's vicious clutches.

"Oh, that's right. I dug up the martial arts skills of the Demonic Adeptss and asked them about them, but they are under Kunlun's care, right? Could I ask for some paper and a brush? I'm planning to write them up in a book."

Qing reveals her misdeeds.

Well, there's no reason to hide the fact that you've been taught martial arts by the demons.

Strictly speaking, the Madou clan was similar to the Kunlun sect's property, so you can't just steal it and keep your mouth shut.

Then it's just stealing.

But Tian Feizi shakes her head.

"What value would the martial arts learned by the Demonic Adepts have for Kunlun anyway? Externally, we already have so many exquisite divine arts that it's impossible for us to master them all. Furthermore, internally, the demon heads' studies were either evil or incomplete, distorted. Either way, aren't they imperfect, inferior forms that invite mental demons?"

Tian Feizi looks worried.

"And how can we trust the advice given by such petty, lowly people? There's no need to dig up their martial arts skills. Well, if it's just useful techniques, then there were those who have mastered the Gwisik method or the Byeokho technique, right?"

It was a suggestion to try digging it up if you're bored.

By the way, the way to eat was to pretend to be dead.

Wall-climbing refers to the martial art of climbing walls.

"Shall I write it into a book?"

"The terrain of Kunlun Mountain, where the original sect was located, was harsh and barren, so if anyone in the world were to discuss the Bihogong and the Guishik method, the Kunlun sect would be the best."

The mountains were high and rugged, so climbing up and down the cliffs was a daily routine. In this already barren area, if a snowstorm came, it was common for them to become cut off from the world, so the Kunlun sect survived by living in exile.

Would it be for nothing that the Kunlun sect abandoned Kunlun Mountain and moved to another place?

Because from the beginning, it was settled in a place that was not suitable for human habitation.

While I'm out, I'll have lunch with my friends.

I recommended it to Tian Feizi Zhenren, but he just smiled and said thank you when I told him to just eat it with his friends.

It was a very generous decision that the scores poured out like rain with just one word, as I was truly grateful, not just in words.

But since we were out for a while, and since we were planning to fill up the 5-day schedule once we got there, we were thinking of taking a walk around the city and having dinner before heading back.

This guy was training hard.

What the heck, he must be frustrated with his pitiful level of internal energy so far. He's a training fanatic who immediately goes into the accumulation phase whenever he has even a little free time.

The mountain was also training hard.

If you look at the mountain, you can see that it was secretly sincere and devoted to training.

But even Heemae was said to be training.

When he said that he was worried because the road to Hwagyeong was blocked, the Taoist monk Boraxin suggested that he try meditating quietly in Suryeon-dong.

So, rather than cheering on my friends who want to study, I can't drag them out to play.

So why not? You should go in early.

At the entrance to Repentance Hall, in a small outpost, there was a Taoist priest named Danlun, who was completely absorbed in reading.

Of course, there was no way that prisoners with crippled limbs will ever be released.

But don't you usually at least pretend to be a little cautious?

Of course, Qing can't hold back when she's curious.

"Can I just leave it like this?"

"Hmm. Go around making some noise."

"I came here openly. If anyone heard, they'd think I was sneaking in by using some kind of stealth technique."

"The madmen won't escape. There's no need to tire yourself out and exert yourself."

"That's a statement that negates the very concept of boundaries. A suspicious person could come from outside."

"If you can infiltrate the inner sanctuary of the Kunlun sect, it would be polite to let them go."

In a way, it was truly a crazy statement.

But I would say that if you were a member of the old school, you have the right to have that confidence.

"Did you have a nice time, Jang Moon-in?"

"Yes. You told me about Repentance Hall."

Qing summarized the conversation briefly.

Danlun Zhenren adds a word to this.

"In addition, the repentance was also practical."

"Is it real?"

"Killing Madou, on the surface, was just piling up a grudge. It also gives them a justification."

On the surface.

In fact, Madu's human relationships were 999 out of 1,000 that lead to profit, so killing them doesn't really create resentment.

But in the world of martial arts, revenge was treated as proof of one's own identity.

Because of the nature of the Madou bastards who uselessly use the term "brother" and "brother" to refer to sworn brothers, they make their revenge known to the public even if they don't want to.

Even though it was the Kunlun School, not all of its disciples were always stuck in the Sun and Moon Mountains.

Also, it was impossible to provide guidance to all the disciples.

When you come face to face with someone who has declared their enemy so openly, you cannot just pass them by because they were shameless and care about saving face, so you have to give them at least one bruise.

This was also the life of Madu, who was full of strong characters.

But what if you lock them up in the Repentance Hall?

"You can avoid the hassle of trouble. It's a pretty good deal considering it only costs about fifteen people to feed."

The more I listen, the more convincing it becomes.

At first, I thought, "What's so pretty about feeding, housing, and clothing these people who deserve to die?" As someone said, I wondered if I was just throwing money away.

I think it's reasonable enough that we could even bring one into our Divine Maiden Sect.

Is it okay?

If you make one and there's a villainess in the old school's confession hall, wouldn't it be okay to bring her there if it's a bit difficult?

But I wonder if it was necessary for the atmosphere of the Divine Maiden Sect.

The Divine Maiden Sect was almost a gathering of true housewives.

Even though I never let my dog go out when I ask to go out, I rarely go out.

Except for the rare occasional trips by older priests, I don't think there's any reason to bring in outsiders to teach our clan, which was already doing well among its own.

And so, Ximen-Qing, no, Cha Xiantian the Annihilaor of Apparatus Formation, returned safely to Repentance Hall.
