\chapter{My Prison Experience (7)}

Five dishes on a large plate.

After eating evenly, there was this much left on each plate, so if you add it all up, there was still enough left over for a whole bowl of food.

I gave the poisonous horse on the right and the adulterous horse on the left a decent amount of taste, so there's still quite a bit left.

"Since you've got some left, why don't you give me a little more? Oh, and were you curious about the other people's stories too?"

"Anyway, let's just use what's left to show our kindness. After all, what were we going to give to the others? At least give them a bowl? Come on. These kids here, I don't know about anything else, but they're incredibly dirty when it comes to food."

The left and right were still after the leftovers of the Qing Dynasty, so the Repentance Hall guys will never compromise on food, even if they compromise on other things.

"What's the transmission? Are you already blinking? I think the door here was open."

Qing opens the door to the brain prison and walks into the hallway.

"Okay, everyone was listening, right? Let's see. We can have about three more. So, Dongpo pork and Baekhwajeongye-"

"Give me, give me!" "Here, here! I'll speak!" "There's someone behind you, rookie!" "Great! It's me, I'll speak!"

Before the introduction of the leftovers was even finished, the noise of people begging for food from all directions was so loud that Qing was speechless.

And that's not all. Bang bang bang! The sound of banging on the iron bars.

It was a very urgent gesture that caught my attention, saying, "Look here."

Even if they had only spared a few people here, the response wouldn't have been this enthusiastic.

"Hmm. What should I do?"

Qing was holding a plate and making a clicking noise for no reason.

He walks back and forth from the entrance of the prison to the back, examining the prisoners.

At the entrance, when I first came in, I saw that there was no one with bad karma in good condition, and there was no one in good condition in the back either.

After digging into the crime for five years and finally letting it go if it's ambiguous, wouldn't it be more difficult for someone to be wronged?

There were seven brain rooms on each side, with one empty room.

Excluding Qing, the total number of people was twelve.

The second from the outermost, right cerebral hemisphere.

An old man with pure white hair sat cross-legged and held a weight, oblivious to the commotion.

What the heck, why was this old man acting so proud by himself? What was he going to do by sitting cross-legged when his danjeon was already shattered?

Or was this perhaps the strategy?

Everyone was screaming for him, but he's the only one doing this, so everyone's looking at him.

If it weren't for his bad deeds, it would have looked something like this, but unfortunately, Qing had a different perspective than others.

"What was it, old man? Are you old and have no appetite?"

"No problem. Go."

Well, what was it that weighs?

"What was this old man? Can someone explain?"

"I, I will tell you."

"That's Salmada! So, thirty years ago…"

"You little punk, you took off your pants and fell down without any sense of propriety or bargaining!?"

Salma?

Since Ximen Surin didn't make him memorize the captured Madu, of course Qing doesn't know.

But I know the general rule of nicknames.

Salma? Two letters?

A nickname consisting of two letters was a very special nickname, a title that only truly qualified masters in the entire martial arts world, that is, masters of the entire country, can have.

So, doesn't that mean that he was once the greatest of the demons who were notorious throughout Zhongyuan?

What was it?

If your nickname was only two letters long, does that mean you won't be so greedy as to lose face over food?

Well then, let's take a look.

The corners of Qing's mouth slightly twitch.

"Salma! Oh, I'm so scared. I'm so scared my hands were shaking, oh my. My hand slipped."

A piece of frozen pork sticks to the old man's face with a crunching sound.

Then the old man opens his closed eyes and looks down at a piece of frozen pork that has fallen in front of him.

The blue human-transcendent vision did not miss the old man's throat as he swallowed without realizing it.

"Oh, oh, oh. Sorry. The old man's energy was so strong that I trembled without realizing it. I can't help it if I drop it. A good person wouldn't pick up something that fell to the ground like a dog or a bug. There's a side room in the back, too. You have to clean up your own room. Sorry for dropping it."

Qing said that with an expression that showed no remorse at all, and turned around to face the iron bars on the other side.

There had been a particularly cowardly voice mixed in since earlier, so Qing had decided to go with this guy.

"Oh, sir, were you curious about my story!? Of course. I'll tell you as much as you want. But, if you tell me a story…"

"I always keep my promises, don't I? Lately, I've been wondering if I really need to. So, do you want to eat?"

"Hehe, my name was Paldaehak. Oh, Your Majesty, just by looking at your eyes, you can tell you're truly beautiful. How can they be so large, so profound, yet so transparent—"

"Okay. How did you get caught?"

"Even though it looks like this, I was originally running a small sect and selling some items I had stolen. But, unfortunately, those items were banned by national law."

"You blatantly broke the law? Did you sell salt or something?"

"No, no, no, that's not it. I sold some opium, but why isn't opium such a serious commodity, and why was it that everyone just takes it and sells it? Why aren't things like cigarettes, which were prohibited by law, sold in pharmacies everywhere?"

"Opium? Hmm."

Qing's eyes narrowed.

This kid was a drug dealer.

But it's a bit ambiguous.

Although it was illegal for civilians to buy and sell opium, it was not actually that difficult to obtain.

If you go to a pharmacy, there was a medicine called opium mal that was made by grinding opium into powder, so if you pay extra, you can get it in chunks.

Then, without fail, a commentary was attached.

"That bastard wasn't selling opium, but a drug called Abu Hwandam that you would inhale and burn. It was famous for making people go crazy."

It wasn't just any opium, it was a real drug that had been properly refined.

"No, it's not. I added some herbs to help someone who was already seriously ill. However, some people bought it and abused it. Why would I care about that?"

"That bastard dug several opium dens in Gansu Island. The government couldn't stand it anymore, so they finally put out a reward notice. At the time, there was talk that he was actually one of the richest men in Zhongyuan. He must have sent cartloads of gold to the government as a token of appreciation. Even that wasn't enough to turn a blind eye, was it?"

"Hmm. He was such a son of a bitch."

Qing nodded.

In Zhongyuan, any crime, even one that involved killing several people, could be compensated for with gold.

Still, it was at an unacceptable level?

What's amazing was that even after all that, he still says that I feel wronged.

What can I do about those who buy and abuse it? In the end, it's not my fault.

Anyway, they give you food.

Come to think of it, I wonder if old Salma ate the frozen pork or not.

When I checked, Salma's cross-legged posture was still the same, and the Dongpa Yukdo was still the same.

Well, a little disappointing.

And then, after I gave the two guys some food as compensation, the plate was completely empty.

Qing takes the empty plate and quietly returns to his room to take his seat.

Then the poisoner starts talking to me quietly.

"Hey, look here."

"Uh. Why?"

"I mean, that bowl. Here, we need to clean the original bowl and return it."

The poisoner stares intently at the empty bowl and swallows his saliva.

His eyebrows twitched.

This kid, do you think he wants to lick the bowl?

Qing, as an experiment, gently pushes a large plate of food towards the poisonous snake.

Then, the poisonous horse's expression brightens.

The plate could not pass through the iron bars that were blocked in a vertical row, horizontal row, and cross shape, so he stretched out both arms to his blue brain jade and grabbed the plate, pressing it against the iron bars.

Well, I don't lick my plate either.

Of course, sometimes when I'm hungry, I scrape it clean and manage to achieve similar results, but I'm still not one to try to lick the dishes with my tongue in front of others.

Well, that's something you wouldn't do even in your hometown.

A poisonous snake with its head covered by a plate and an iron bar between them.

As Qing was clicking her tongue, saying that she had seen such a filthy sight, this time, there was a gulping sound from behind her.

"What, you rascal, you want to lick the plate too?"

"Ahem. Those Kunlun Malko bastards only eat bland things, so what the heck? Damn it. It's not salty or sweet, and it doesn't have the kind of flavor that makes people go crazy."

Certainly, boiled chicken with dumplings was a bit of a bland meal.

It comes out well, but it seems like they don't give spicy food.

For some reason, he was so obsessed with cooking that he rushed into it.

He said that the only joy in his life in Repentance Hall was eating, but perhaps it was also because he was always exposed to bland food.

"Huh. He's not a dog, so I just gave it to him once to see if he'd really lick it."

The poisoner stopped there.

But that too was only for a moment, and the plate moved up and down, left and right, as if it was going to keep licking it for now, regardless of its pride or anything.

"If there was a going, there must be a coming back, right?"

"Hmm. Is this okay? The kid next to me was a so-called "So-Cham-Myeong-Ta" (a name that means "small, dark, dark-skinned, evil spirit")."

"Why were you selling someone else's story so recklessly? Why don't you shut up right now?"

The person in the next room, So Cham-myeong, immediately becomes serious and starts to speak.

But the adulteress didn't care.

"He's the guy who would kill any kid who laughed at him, and beat any kid who cried to death."

"No, why?"

"No, has Kang-ho been around for a day or two? Are there just a few kids who were addicted to killing people? What's the reason? They probably just did it because it was fun."

If I say that seriously, will you spare my life?

Then tickle them and make them laugh.

Those who don't get tickled were tortured by having their bones squeezed, being put in and out of water, and other means of making them cry.

In the end, you have to kill the one who got caught to feel better.

"The one who laughs has his mouth ripped open and hung up, and the one who cries has his eyes gouged out and hung up. You did that shit, so why didn't you get caught and get away with it?"

He has a flaw.

"Is that so? This time, it seems like the guy who deserved to be disabled has been disabled for no reason. Do you have anything to say?"

"Ha, that's ridiculous. Do you think I'm some kind of murderer? I'm a swordsman, a swordsman. I only kill those who deserve to die."

"Huh."

"Of course, can anything a person do perfectly? I've made a few mistakes, but the trash I've cleaned up far outweighs the occasional mistake. If we're going to judge my merits and demerits, I'm hardly worthy of being called a chivalrous man."

Qing checks with the cheating horse again.

"Is that right?"

"What the hell. When that bastard killed someone and hung them, he thought it was a sin and beat them up, didn't he? He killed someone who shit on the street, a corrupt merchant who swindled him, a doctor who didn't come to see the king, a thug who was mean to the elderly—that bastard just picks out easygoing bastards and kills them. That's not even close to killing him."

Hmm. Well, I guess so.

There were still three dishes left, so I was able to gather the stories of the three through the chatterboxes on the left and right.

With this, I was able to gather the grievances of nine people, including Salma, so there really isn't a single one who hasn't been wronged.

From saying that I am innocent, to saying that I am guilty but not to the extent that I should be locked up like this, to one guy saying that he just did what he was told and his superiors were fine while his tail was cut off or something.

They say there was no grave without an excuse.

Still, it was not difficult to figure out the truth because the very subjective self-defense was followed by objective criticism, perhaps to indicate that I cannot be the only one who was an asshole.

There were three guys whose stories haven't been sold yet.

At this point, it's pointless to even listen.

He must be a son of a bitch and feel wronged.

Of course, it might not be true, so you'll have to hear it to know, and what's the big deal about hearing that?

Dinner will be served anyway.

First, you have to tell me everything and show me how to cook. Then, I'll tell you some of my money.

It's a bit of a petty method, but right now, increasing the size of my internal energy was the priority.