\chapter{My Prison Experience (8)}

The land of Qinghae was a land with unusually long days, with sunset past 6 o'clock even in the middle of winter.

Above, a crimson sunset illuminates the inside of the prison through a small window tucked into a corner, avoiding the bedroom tent.

It was also a time when all the prisoners in the prison were just waiting and waiting.

It's dinner time!

In just half a day, Qing perfectly understood why the prisoners in the penitentiary were so desperate for food.

There's nothing to do!

There's nothing to do!

Ah, there really was no pleasure here other than eating.

If they had forced them into labor, this would have been completely neglect.

They say that when people have their basic necessities taken care of, the thing they fear most was boredom. So, this was how they were causing suffering.

The Kunlun School Taoist priests also do quite a bit of it.

Still, the situation was different for Qing.

Since your danjeon was fine, you can at least do some energy saving.

It's a frustrating and uninteresting game because the efficiency was a mess due to the status window.

But there's nothing to do.

They keep nagging me to do some math on the left and right, but am I in a position to play some primitive, ancient, uncivilized, handmade board game with the madoos?

Anyway, I managed to endure the training that seemed like an eternity.

In the end, the sun sets.

And so fate bursts through the metal doors of the confession room.

"Today we have steamed carp and squid."

That fate was in the form of steamed carp and early fish.

The prisoners' expressions darken rapidly, as this was a fate that no one wanted.

Carp was not tasty enough to be steamed.

However, it was also a lucky dish that had to be served on the Lunar New Year table, even if only as a decoration.

And the first one is, um, egg fried rice.

Danlun Zhenren began to walk around Repentance Hall, scooping out a carp from a large bucket and a pile of dried pollack from a large basin.

By the way, isn't that bowl the one we used for lunch?

He licked it clean somehow, but was that the dishes?

Come to think of it, it seems a bit odd for a Kunlun sect Taoist to even wash the prisoners' dishes.

The single-wheeled Zhenren, who had made a full circle like that, stopped in front of the Qing's brain jade.

And then he pretended to think for a moment-

"You stayed quiet even though the door was open. I'm glad you did. I'll give you a meal."

"Wow, thank you!"

The prisoners naturally look dumbfounded.

In the front room, the dumpling ears were so ridiculous that they wouldn't dare to get angry and talk back.

"No, shit, you're going to keep cooking for her until she fixes that damn door? What the hell were you talking about?"

"This man, despite the fact that the prison was not locked, did not dare to escape. This was a remarkable act of deep remorse and a willingness to pay the price for his sins, a fundamental human virtue. Therefore, I wish to fully commend and reward him."

Danlun Zhenren has a bitter smile on his face.

Well, the Taoist priest was really enjoying himself.

"You have been imprisoned for fifteen years and cannot stand to see others profiting from it. Your heart was still stained with the same color that you have not been able to wash away."

The atmosphere suddenly cools down.

A silence so thick that you can hear the rustling of hairs, a silence so full of fear, surrounds the hall.

What? All of a sudden? Is it possible that the Danlun Zhenren felt this much pressure?

"I gathered you all in the Hall of Repentance to cleanse your hearts and truly acknowledge and confront your past sins. But since that hasn't happened, we all deserve to be punished together. There will be no tomorrow."

There were awe-inspiring expressions of shock and horror.

Qing's eyes shine.

No, solidarity responsibility here?

It seems like this isn't the first or second time this has happened.

The prisoners only stared at the dumpling ears with a murderous look on their faces, and no one dared to protest or spit.

In the silence, Danlun Zhenren puts out a cooking bowl.

"Ah. I'll help you."

Qing naturally opens the door and goes out.

That girl, how long has it been since she was praised before she walks out? She's not some kind of idiot.

As the prisoners freeze even more, Qing personally takes the dishes from the cart.

But the single-minded Zhenren just nodded as if it was natural.

The prisoners forget the morning they were blown away by the indescribable absurdity and just gape.

Qing covered the dishes he had finished eating and placed them on the cart.

Then, the trembling eyes of the single-wheeled Zhenren.

"You ate all that? Are you human?"

"If you try, there's nothing you can't do, right?"

"I guess I'll have to increase the quantity tomorrow."

"Hey, no. Actually, I thought lunch would be too much. It's too much. I think it'll be fine if you cut the number of meals down to three."

Five bowls of food, five plates of dishes.

Even if you reduce the number of meals there to three, it's still not enough for one person to eat in one meal anyway.

"Okay, I get it. Is this too much?"

"Hey, was there a give-and-take policy? If I get hungry in the middle of the night, I'll have to eat it as a midnight snack."

Five meals out of five were lunch.

Dinner was naturally more than that, so it's natural to assume that there were five meals and seven dishes.

While we were at Repentance Hall, he said he would feed us until we were full, and it seems that Jangmun Jin-in was really trying to keep his promise.

Are you really trying to blow it up?

Even though I have a bit of a picky eater, how can I eat five to seven meals?

Of course, Jang Moon-in ordered that the pretty little sister be given the leftovers as a favor to her precious guest.

"Oh, could you give me a little bit of that first? I'll be in Repentance Hall now, so I need to see what the food there tastes like."

"I have many wishes."

"Oh. The carp was fine."

"Tsk. Okay."

He was a simple-minded person who gave a handful of advice while responding bluntly.

"Okay. Let's do our best."

"Yes, I will do my best!"

And then the endless "Good job" appears.

And then the single-wheeled Zhenren leaves.

And then the spiral?

The life of the blue, the joy of life, the reason for the blue's existence.

Everyone was here to eat this dish at this moment, so why hesitate or delay?

I can understand why the prisoners' faces darkened at the dinner menu.

It's well-cooked fried rice with eggs.

But did you hit the liver too hard?

The broth in the steamed carp looked so clear. You could tell just by looking at it that it was bland.

Qing realized that the Repentance Hall diet was low in salt.

Well, how much saltiness would a day laborer who doesn't do anything and doesn't even sweat need?

One could say that one can feel the consideration of the Kunlun sect Taoist priests who want one to live a long life in Repentance Hall.

So, the prisoners' attention was inevitably focused on the situation of the Qing's leftovers.

"Whew. I'm full."

Since there were places where the leftovers can be used, I didn't cram them in like I did for lunch in Qingdo.

"Well, well, I have to hear something today. I think there were three people left who don't know the story."

"That guy over there was Chohwan-" "Chohwan Salgwi! Chohwan Salgwi!" "That kid was a really bad kid!"

The cheers were like a fiery blast as they shouted and shouted that they would talk to each other.

"Shh. You're all so disrespectful, like the little bastards of Madou. You put yourself first, right? Of course, if you don't want to talk, there's nothing I can do."

Then, a few poor people who had their stories revealed in exchange for doing all the dishes shrugged their shoulders with pitiful expressions.

Anyway, it's not like Qing will be fair to the madou.

"Then, let's start with the old man and listen to his story!"

So the remaining three.

Old killer.

The most unfair type was false accusation.

As my notoriety grew, there were a lot of bastards who committed murders by selling my name, and what I did was only a part of that.

A famous sex addict and assassin.

For some unfair reason, those girls enjoyed it too.

And another murderer.

I too claim to be a victim of the world, a monster who was inevitably created through a terrible childhood.

It was a feeling that brought to mind a proverb from my hometown.

There was no grave without an excuse.

How was it that out of the twelve guys in Repentance Hall, excluding old Salma, all eleven were complainants of injustice?

Of course, it's not surprising since Qing always had that thought.

Aren't people only sorry because they have been punished, and only one in a thousand people actually regret their mistakes?

Regret and repentance were completely different concepts.

Now that the story of selling fish has been told, it was time to start seriously pursuing the original purpose of fishing for martial arts.

Nothing else was needed, just the internal energy method.

My internal energy was lacking.

Right now, you were the Great Swordsman of the Transcendental Flower Realm, the Super-Joint Flower Realm, the Super-Word Sword, and the Great Swordsman of the West Gate, but what will you do when you become a Hyeon-gyeong later?

A Hyeon-gyeong with internal energy on the level of Hyeon-gyeong?

That can't be possible, right?

This useless, ineffective weapon (ineffective weapons can be very, very, extremely frustrating) was only useful in the short-lived times that pass by anyway, but as your level increases, it becomes useless.

So, we need the inner strength method.

I need to learn this and that and increase my internal energy.

but.

Qing, whose intelligence increases significantly only when dealing with bad guys, suddenly uses his improved brain.

I can't say something so outright like, "I'll give you the leftover food scraps in exchange for your knowledge of the inner power method."

If they knew that I was targeting the internal energy method, wouldn't they try to raise the value as much as possible and get a large price?

Besides, it could arouse suspicion.

Now that I think about it, if it were said that he was a spy of Malko, a fake criminal who was put in by the Kunlun Sect to extract martial arts, wouldn't it be completely empty?

So, somehow, I have to fill the child, and they have to say, "Shut up and give me that plate of leftovers, so I can call out my martial arts first."

You don't need much.

Just one guy.

If just one person brings it up, everyone will cling to it, saying, "Please buy it, please buy it."

Here's a woman who throws away leftover food waste and then tries to take credit for other people's achievements in exchange for the food waste.

It was a level of evil where you can't tell who was the master and who was the Taoist.

"Hmm. There's a lot of food left."

"If there were any left-"

"Oh, what comes must go, right? Even if I've ended up like this, I absolutely can't give up on that. This isn't a question of others or me. It's proof that I'm alive, and I'll live on. So, it's a question of me, mine, living. It's as natural as breathing and eating. If it weren't natural, there would be a problem, right? Do you know what I mean? You'd be better off opening that toilet lid and throwing it away. There's no such thing as meaningless happiness. Otherwise, you'd have to wait for it to come back because you opened that toilet lid and threw it away."

Everyone had an expression of ignorance on their faces.

Well, that's because Qingdo doesn't know what he's talking about and just talks nonsense.

It might sound silly to others.

But isn't it clear that they won't give it away for free?

"No, shit. What the hell were you asking for? Look, does anyone here have anything?"

"I'm not taking it because I need it. Giving away what's mine for free is—wow, creepy, creepy, horrifying. How could you just hand over what's mine? Does that make sense? I can take anything and give it away. It doesn't matter if I need it."

But somehow, as I kept talking, a coherent logic emerged.

"Hmm. That's true too."

Even until someone agrees.

Then, the dumpling ears immediately start cursing loudly.

It seems like there's a lot of bad feelings about what happened at lunchtime.

"It's a fucking hit, but it's a fucking hit. Isn't that why that fucking bitch was stuck here?"

"Then? We've come this far, so why bother showing kindness? What will you get for showing kindness here? Then why waste it here when you can just spend it outside?"

"Ha, you fucking bitch, damn it."

A dumpling ear that has nothing to say and just swears.

Qing said, twisting her lips as if she was looking at me.

"Okay, so I'll take anything. What was it at lunch? The above? Okay. Tanseok? I'll take it as a special treat. If you don't have anything to offer, just cut off your finger and give it to me."

If you don't have it, you want me to cut off my finger and give it to you?

The prisoners in Repentance Hall were all convinced.

I was wondering how a young woman came in, but this was the first time I've seen such a vicious woman.