\chapter{My Prison Experience (5)}

There were many ways to silence a person, but none of them were as effective as the one presented.

The dumpling ear prisoner was no exception.

"What. What. What were you asking for now-"

"Then don't worry about it. Just blow it off and I won't have any regrets."

What was there to regret about?

But the dumpling ear prisoner was a pity.

Why was this kid so gutsy?

What do you plan on doing if you reveal that the door was actually open?

But now that it's been less than a day since I entered Repentance Hall, I might still have some time.

Now that my life as a drone was over, I might just be in a state of despair.

Or maybe he's already lost his martial arts skills and thinks that going outside won't do him any good.

Anyway, if you're a loser who comes to Repentance Hall, you're bound to have a lot of grudges.

"What do you want?"

"No. I said Jessie. Can you really be so immoral? Or do you not know what Jessie means?"

"Ahem. Then. Well, even if it's a special meal today, well, yeah, I'll give you a special dinner too."

The dumpling-eared man's expression was extremely tragic.

If you listen to the expression and tone of voice that says he's willing to give up lunch and dinner specials, doesn't it almost seem like he's prepared to make a huge sacrifice?

With the same determination as Makya, who said he would jump into the molten metal to complete the new sword, or the commander, who said he would stay behind alone with the bomb detonator to save his party.

Why were you saying you'll give me food like this?

Almost as if he were willing to sacrifice his life.

Of course, food was important, but to this extent?

But the prisoners seemed to think differently.

"Ugh." "Special meal…!"

"What was it, Uga? Did you find some kind of weakness?"

"What, you want me to show you my naked body? No, what, what use would a bastard like you have to be to see a woman's naked body? He's not even going to stand up anyway. Hehe!"

Everyone's reaction would be, "What the heck, this was happening! Amazing!"

After all, for the prisoners of Repentance Hall, meals were the only happiness left in life, and special meals were a precious treasure that they waited for all year long, even though they came only a few times a year.

Among the many sounds, there was one that bothers me.

"Wait a minute, what were you talking about?"

"Why were you pretending not to know? No, there's no need to get rid of a woman. Hehe……."

I heard that they broke his danjeon, cut off his meridians, and even castrated him.

Somehow, everyone's attitude was so calm.

The Kunlun School Taoist priests also have a hard time.

As a guard, you have to provide food for the prisoners, but as if that wasn't enough, you have to castrate the prisoners?

"Hmm. So, did you remove the pillar or the egg? No. You removed the egg, so you're being docile. Then, you saved the pillar? No. What's the big deal? Don't worry. Just eat the special meal, and let's talk. What on earth did you do to become a eunuch and be locked up in the repentance room?"

But the chatter continues unabated.

In Qing's hometown, it was a never-ending stream of information, what the technical term for it was local broadcasting.

"Heh. That pillar was safe. If you touch it, you'll die or something. But you come all the way here and you still care about that? Are you some kind of crazy woman? Is that really that important?"

"Anyone who lets their inner strength drain just to try to hit someone once was a retard. That kind of person deserves to be hit."

"This kid was caught fucking a woman and now he's talking really badly to her."

Hmm. Maybe it's because everyone was so talkative.

Anyway.

Qing turned off her guard and looked at the man with dumpling ears.

The man with the dumpling ears let out a sigh and said this.

"I feel wronged."

Qing sees the evil deeds of the dumpling man.

Of course, it's a bright red color.

Didn't the Danlun Zhenren explain in the first place that this was called the Tamjodong, and that they would investigate sins for up to five years?

Even after five years, if the person was still unable to be found guilty, they were simply released.

What that meant was that the kids who came into the repentance center were real bastards who had gone through a lot of verification.

"Unfair? Why? Did I get framed?"

"I simply wanted to live. I couldn't just be captured and killed, so I resisted. Can it be considered a crime for a civilian to protect themselves?"

"That kid's acting like that again. Normally, even if you're trying to get rid of a minor offense, you don't go as far as to kill a child just to get rid of the root of the problem."

One of the prisoners snorts and adds an explanation.

He sees the dumpling-eared man again.

"I didn't want to, but I had no choice. Should I let you live because you're young? If I get old and come back to seek revenge, should I just get stabbed and killed? It's only natural to root out the root of the problem."

"I think I know something."

"Right? You can understand, right?"

"Is it just the child's problem? If he had a close friend, he might come for revenge again. What about leaving his friend alone?"

"Of course I couldn't just leave it alone. I wiped out all the kids who tried to stop me, all the guys who stared at me with their eyes wide open. I uprooted them all, completely."

"Those people probably had families. In the end, if they didn't want to get caught, they'd have to beat up everyone in the neighborhood, right?"

"Oh, shit. I was alone, and those bastards came at me in a horde. Those vile bastards."

The dumpling-eared man grits his teeth.

"Why did the fight start in the first place?"

"Huh. It wasn't something that big. As I was leaving quietly, those kids started harassing me. I just fought back."

Here again, the commentator says a word.

"That kid tried to run away after stealing my food money, but I ended up beating the neighborhood lord's son to death with one punch."

"I swear on my life, I had no intention of killing you. How could I have known that bastard was that weak? You don't even realize that those bastards who swarmed me when I was just a bunch of idiots fighting each other were being beaten. If you're going to draw your sword, you should have been prepared to get stabbed, you fucking idiots."

So, to sum it up.

It seems that he was trying to run away after stealing the money for his meal, but was stopped by a local official who happened to be at the inn.

In the first place, would a petty brat who would steal food money have stayed still? Of course, he would have come out first with a knife or his fists.

Then, it seems that he killed the son of the military governor, so of course the military governor would have been furious and rushed at him.

They kill everyone, and because they were afraid of the consequences, they kill their families and friends, and then they end up having to kill more family members.

If you repeat that, of course all the sects in the neighborhood will chase you with their swords in hand.

As a result, his dantian was broken, his limbs and veins were cut, and his testicles were removed, after which he was permanently isolated in the Kunlun Sect's Repentance Hall.

Qing blinked her eyes.

Umm. A very bastard.

Where on earth was the injustice here?

Of course, Qing doesn't necessarily feel curious.

"No, shit, what the hell was wrong with you?"

"Damn it! It was only three silver coins, three silver coins! If you're going to pull out a knife for that kind of money, you should've been prepared to die! What can I do when that bastard attacks first! Are you telling me to just sit still and die?"

"You were trying to save just three silver coins, but you ruined your life. What were you complaining about?"

"If you don't know, just shut up! You throw away trash that looks like it was eaten by a dog, and I wouldn't feel good about taking money from you. What? Three silver coins? Do you think people were pigs and dogs? You're talking like real dogs and falling down!"

"Huh. I ate expensive food without even knowing what I was eating, and that's how I ended up like this."

"What, you think this kid was a sweetheart?"

"Isn't that a completely cheap life? One silver ja for the dantian, one silver ja for the main vein, and half a silver ja for the testicles, making three silver ja. If you were caught stealing three hundred gold coins, it would be different. It's so unfair that a punk becomes disabled for a mere three silver ja. If I were you, I'd bite my tongue and die in shame. Don't you all feel the same way?"

"That's right! That's so fucking true!"

"This fucking retard!"

Laughter erupts inside the chaotic Repentance Hall.

The man with the dumpling ears glared at Qing, his face turning red and trembling.

"What? What were you going to do if I stare at you? Okay, I'll show you my kindness. I'll stay still here, so you hit me until I'm relieved. I told you to hit me like a man, right? Surely you're not some idiot who can't hit me even when I'm offering it to you, were you?"

"Kuuuuu, this bitch was really something."

"If you want to enter the Repentance Hall, you have to do at least this much, right, then!"

On the far left and right, people were laughing so hard they couldn't even breathe.

The man with the dumpling ears looks at me with eyes brimming with resentment, as if he's waiting to see what happens.

But what?

Even if a man with no dantian and severed meridians were to stare at her or even if he were holding a sword in his hand, there was absolutely no reason for Qing to be afraid.

It might be a little scary if it's a gun.

Bang bang!!

At that moment, there was a rough sound of iron plates being hit.

Then, the prisoners who had been giggling and teasing him suddenly shut their mouths as if nothing had happened.

-Do you want to starve on New Year's Day? I was thinking of letting it go since it's an auspicious day, but you're really excited?

It was the voice of the single-minded Zhenren.

In Qing's opinion, threatening someone with food was a truly lethal and petty thing to do.

But it was a very quick fix.

After a while, it became quiet again, so Qing, who had lost his temper, quietly returned to his bed and practiced the Mansangyeoilsingong.

How much time has passed like that?

He was sitting cross-legged on the bed, not lying down, how amazing was that, Qing sniffed.

What was it, that fragrant and delicious smell?

As expected, the door opens and the distinctive sound of small wheels rolling approaches.

Food, it's food time!

Qing, clinging to the bars, looks towards the entrance of the prison cell, and sees the hands of all the prisoners holding onto the bars in the same posture.

"Today was New Year's Day, so I'm having dumplings and steamed chicken. Don't throw away the bones; just leave them out."

Danlun Jin-in puts a bowl down on the flat hole at the bottom of the iron bars, places a chicken on it, and then picks up a handful or two of dumplings and sprinkles them on.

Qing-i looks at it, what's this? Isn't the food surprisingly good?

On the upper level of the food cart, which surprisingly looked similar to the ones from my hometown, there was a huge basin filled with chickens, and another basin filled with dumplings.

There were numerous lids on the lower floor.

"Hey, look here. That thing over there was covered up…"

"It's not yours, so don't worry about it."

It was the blunt answer of the single-minded Zhenren.

According to Qing's interpretation, who had already become friends with Danlun Zhenren through magic, it was not that he has a particularly cold attitude, but rather that he was just that kind of person.

Then, the moment came when the food cart stopped in front of the Qing's brain jade.

"Look here, Dojo."

The dumpling ear man calls out to the single-minded Zhenren.

The single-minded Zhenren looked at the man with the dumpling ears from afar.

"What's going on?"

"That's it. Hehehe……."

And then he looks at Qing and smiles sinisterly.

"Hey, girl. Don't you have anything to say to me?"

"Ah. You're going to come out like that? Oh, come on."

At first glance, it seems like a threat to at least apologize or else he'll blow it up.

Shouldn't this be done to someone who can be threatened?

After Qing smiles back, she looks at Danlun Zhenren with a pretty smile through the open eye sockets of her single-faced mask.

"Master, you left the door unlocked earlier. It's open right now, isn't it? Like this? It's just opening?"

Qing opened and closed the iron door, then opened and closed it again just as it should have.

The man with the dumpling ears looks shocked.

And as I suddenly stuck my upper body out into the hallway, I saw prisoners in the prisons on both sides with their mouths wide open.

The shocking truth was obvious.

Did you know the door was open?

But you're saying that you're going to do it again?

Whether the prisoners were surprised or not, their eyes, sparkling with playfulness, turned towards Danlun Zhenren.

Danlun Zhenren stood there for a moment, as if thinking.

Soon, he nods his head and says, "Hmm."

"You didn't escape even though the door was open. You have no intention of escaping."

"Of course. What about escaping? If I go out, the Kunlun sect priests will be all over me."

"I get it."

And then, Danlun Jin-in pretended to look at the door.

"The door was broken. There's nothing we can do. Stay still."

"Yes! I will be very quiet!"

That's the end?

The door was broken and won't lock?

Just be quiet and that's it?

Qing proudly looks over the prisoners.

What should I say about the prisoners' expressions?

It was truly a pity that there were no cameras in this ancient, primitive Zhongyuan world.

Qing takes it a step further.

"But what were those plates down there? Are they perhaps food for the Taoist monk?"

After a brief pause, the single-minded Zhenren-

"Yes. But since you were honest and confessed even though the door was open, I will reward you."

This was why you should associate with smart people.

If you pretend, you'll pretend, and since you're quick-witted, wouldn't things go well together even without saying anything?