\chapter{My Prison Experience (4)}

From the first to the second, from the second to the third, from the third to the fourth, from the fourth to the fifth, from the fifth to the fifth, was it the fourth or the fifth that was higher?

Is this supposed to be twisted once, or just kept going in a straight line?

I kept nodding my head to check the location of the blood vessels, but I don't remember what I learned.

You might say that the unmanned person was wandering around without knowing the bloodline, but that would only make Qing feel wronged.

Even if you say that they know all the blood points, they were the only ones who know how to memorize them, and even though Qing was a female doctor, she hasn't learned acupuncture yet.

Just because you were a martial artist doesn't mean you have memorized all the blood vessels in your body.

Usually, in most cases, I didn't even know the main passages through which the mind method I had learned passed.

If you learn martial arts alone, it was difficult to know the exact location of the blood vessels.

The crude drawings of the human blood vessels in Zhongyuan rarely give us a sense of how deep they are.

Of course, unless you were studying ascension, the flow was not that complicated anyway.

If you lead the bet to an easy path around that point, the answer was Gugugupun, so there were no particular problems.

Of course, the study of ascension was extremely complex.

However, such difficult and complex new techniques cannot be learned alone.

When you were introduced to this kind of new martial art, the master places his hand on your back and moves his energy to give you a test run and open the way in one go. This was a noble technique called Jingi Doin.

And Mansangyeoilsingong was one of the most outstanding martial arts in the entire Western martial arts world, and was a purple-colored divine art by Qing standards.

Moreover, since it was an old martial art, the terminology was old and dead language from a long time ago, and it was a translation of the Indian language into the Western language, making it doubly bizarre.

In other words, it's very, very complicated.

In the first place, Amukhaprap never thought he would learn the Mansangyeoilsingong that Qing had lent him.

Of course, I already had my own studies, and I didn't think that Qing, who already possessed many divine powers, would bother to scatter his own to learn the wisdom of the ten thousand and one.

I thought I would learn it to some extent and use it.

But Qing was hungry again.

When I was at my peak, I thought, "What do I need since my internal energy was already full?"

After entering the Hwagyeong, I felt a sense of crisis that if I continued like this, I would end up becoming an ordinary Hyeon-gyeong, and I had no choice but to turn my attention to the Naegongsim method again.

so?

AC, I don't know.

The beginner doesn't have to go through many training points.

I've accumulated a lot so far, what were you going to do with it?

So while the prisoners were raising their voices and bragging about their crimes, in the luxury bunk behind the tent that covered the bedroom/toilet, Qing opened his eyes cross-eyed and unfocused, feeling an endlessly dirty sensation in his brain.

It's a strange feeling that's so filthy it can't be expressed in words, but it's not painful or anything.

Ah, I really don't know how to express this… … .

So even after the study of the complex Mansangyeoilsingong took hold in my head, I just lay in bed with my eyes wide open.

The great Buddha, Vairocana Buddha, or the main Buddha in the Chinese language, was the universe itself.

Thus, everything in the world was the original Buddha, the sky, the earth, even a single dry leaf rolling on the roadside, all were Vairochana Buddha itself.

So, all things, everything in the world, was the one and only Buddha.

The Mansangyeoilshin Gong, which was created from such an image, refers to the Danjeon as the Lotus World, which was the center.

And the middle stage was the truth, the sun that was always there. The flow of true energy was the shape of the truth rising from the lower stage to the middle stage, the lotus world, and the sun that illuminates all worlds.

And a three-dimensional flow that branches out into countless branches, circles the body, and reaches the middle ground again.

Perhaps because it was a Western martial art, it developed in a completely different direction from Zhongyuan martial art, which was a single stroke of left-right symmetry.

In fact, Mansangyeoilsingong was not a Western martial art, but a Cheonchuk martial art, but Qing had never heard a separate explanation.

I'm glad I learned this at the training center.

If I had just tried to master it, it wouldn't have been enough even if I had trained all the blood vessels in my body.

Meanwhile, there was a new member in Qing's dantian.

It was a very shiny and dazzling newcomer.

The most striking difference between Zhongyuan Buddha and the Indian Buddha was their splendor.

Because the Buddha of India wears jewels instead of clothes.

The Pure Land of Buddha was a luxurious paradise, a land made of gold and jewels, where the most precious wine flows like water and delicacies gush forth from the mountains and the sea. (However, there were no women.)

The Mansangyeo Ilgi enters the Dantyeon with the sound of jewels rustling.

A garment that falls over the left shoulder and coolly covers the right upper body. Can you even call that clothing?

It was a luxurious set of various rare jewels strung on thick gold strings like a curtain, as if ten gold warehouses had been burned down to make it one set.

The magicians suddenly woke up and their eyes lit up.

Look at that, that, that, that, look at what he's doing.

That extravagance and obscenity, that's ten percent, absolutely on our side.

It's certain that we finally have a proper queen on our side!

It was when the poor, evil magicians who had been persecuted and oppressed were about to rush in, thinking that they should at least give them a washcloth.

Over there, in the sunlit VIP seat, two immortal beings raised their hands.

The magicians, as if they were frozen in place, turned their heads unnaturally and giggled.

The old man, who always held his weight with a serious expression, was now raising his hand with a rare bright smile.

Next to it, an elephant shook its trunk, a dragon shook its tail, and a dragon seated on its head flapped its hands.

A smile spread across the room as Mansangyeo Ilgi, who had discovered him, and his perfectly white teeth sparkled.

A dramatic reunion of the legendary heroes from India!

The Taoist jin qi, who had been wary of such extravagance, soon smiled warmly with relieved expressions.

Among them, a very excited Hwanhee Jinki suddenly runs in and shakes his jeweled clothes while looking at the precious gold and jeweled accessories.

Mansangyeo Ilgi looks at Hwanhee Jinki, who was making a fuss and lifting the hem of her clothes, and takes out a large blue jade.

Perhaps there was some kind of communion that transcends Taoism and Buddhism between the two, the Hwanhee Jingi that seeks to embrace everything as one and the one that identifies all things as one.

The expressions of the magicians looking at him rot.

They were all fighting amongst themselves, they were all fighting amongst themselves.

How can I live in this dirty world, what suffering can I have if I meet the wrong master?

The biker in the next town just pierces the upper body and pulls out lightning bolts when he's even slightly upset, but some people get caught up in the wrong owner and just watch the situation closely.

The nervous expressions of the magicians were directed towards the corner of the dantian, the most damp and gloomy shade.

And pat pat thump!

The Heavenly Demon True Qi was smiling.

But sometimes I shed tears… … .

Black tears dripping down from the eyes with teardrop-like pupils.

Today too, tears were flowing down my cheeks.

What if you learn some kind of technique?

After that, the amount of magic that can be used increases by just a little bit, like a sparrow's tears.

"Hey, newbie."

Qing roughly knew the capacity of the complete Pacheon Magic.

Even if I added up all the internal energy I had now, it wouldn't even be enough to do one-tenth of the amount of magic power that Heavenly Demon True Qi had, it was a huge flow like the ocean.

"Shh, newbie, newbie?"

It's a bit unsettling to see the once vast ocean compressed into something the size of a booger.

But there's no other way. It doesn't really interfere with the development of internal energy.

Well, if I could just break the seal, it seems like the problem with my internal energy would be solved in one go.

Then, wouldn't it be possible to have internal energy at the level of a life and death mirror, rather than a reality mirror?

"Hey, this kid, hey, newbie."

But it looks like it happened.

A pitch-black river with countless pupils?

Hmm, that would be totally cool.

Doesn't this move?

Qing tries to poke the Pacheon Magic Aura attached to her dantian, but when she intentionally touches it like this, the capacity doesn't increase.

It only increases slightly when I learn a new martial art or when my danjeon automatically starts to ache once in a while.

If you stretch it out a bit, you can shoot rays with your fingers too.

Because the Heavenly Horse Roll was so useful in so many ways, people usually don't even use the Light Wave to save on the Heavenly Horse Roll.

What on earth was the principle behind its increase?

I have no idea.

"Hey, you punk! When people talk, listen!"

Someone shouted from beyond the curtain.

Qing, who had been feeling down and distracted by the aftereffects of the brain-sucking learning method, finally clears his blocked ears.

Of course, Qing didn't know that he was really calling her.

Since you said you were a newbie, I thought there was another guy who had just joined besides me.

"Hmm? Me?"

"Oh, you son of a bitch, you're listening to all this nonsense! Yeah, it's you, you son of a bitch!"

"No, why were you so angry? People can have other thoughts, but if you get angry, you're only harming yourself."

"Kwaaak!"

The sound of banging against the wall echoes.

Not bang bang, but kong kong.

At the sound of something cute, Qing peeked her head out from behind the tent that covered the bedroom and bathroom.

He was the guy in the prison right across from me.

Is my fist precious, or was the wall precious and I want to protect it?

The fist suddenly slowed down just before hitting the wall, but the calluses on the protrusions on the back of the hand were thick.

Both ears were attached to the head.

A callused fist with dumpling ears?

Even so, what does it matter whether a guy who has to climb over the bars one more time has dumpling ears or fairy ears?

"Why? Why were you calling me?"

"I can't say right now."

This time, Qing's eyebrows twitched.

What kind of guy was he, calling people over?

"What were you talking about? I can't say anything."

"Because, um, I can't say that right now."

What the heck, was this some new type of bullying?

A trick that makes people feel frustrated and makes them explode?

It was the moment when Qing was about to say something.

"Ah, that fucking annoying kid!"

"What were you doing that makes people curious!"

"Why don't you stop talking right now! I'll rip your mouth off."

Here and there in Repentance Hall, voices of condemnation on behalf of the youth could be heard.

The man with the dumpling ears on the other side of the iron bars just kept his mouth shut in frustration, and then suddenly he started hitting the wall again.

Boom! Boom!

This time, it was a government that has truly gained power.

For someone with no dantian and no meridians, his power was quite impressive.

The callus was torn and blood was oozing out.

What? Sudden self-harm?

As I was watching the spectacle in my bored car, a man lifted the tent and stood right in the middle of the wall.

And then he lifts it up and writes on his bloody fingers.

Only then did Qing realize the man's intentions.

Oh, if you stand there, only the people in the prison on the opposite side will be able to see you.

I think he said he couldn't talk now because he accidentally drew my attention while calling me to tell me something secretly.

Qing looks at the man's palm.

Your room.

It's two characters because my palm was narrow.

Qing nodded, indicating that she understood.

The door opens.

What else should I say?

Of course, Qing was in the middle of a confession, so of course he didn't lock the door.

The dumpling ear prisoner seemed to think that it was the Danlun Zhenren's mistake.

He writes again.

Jailbreak.

The dumpling-eared prisoner squeezed the back of my hand tightly, as if he was running out of blood after writing that much.

Help each other.

Let's go out together.

otherwise.

I will spread the word.

The door was open, so let's escape together.

Or else I will inform the Kunlun sect Taoist priest and have him lock it.

Qing suddenly thought, oh, I have a feeling this was going to be really fun.

I was already bored, so this was good.

Qing said with a wicked smile.

"Isn't the balance a bit off? Even if I get down on my knees and beg, they won't listen. There must be a return, or a return."

The dumpling ear prisoner made an impression on him.

Qing-i proudly utters the word, which was so destructive and dirty that it was tacitly forbidden in the upper world.

"Okay. What's in it for me?"