\chapter{My Prison Experience (2)}

They said that preparations were needed in the repentance hall, so I will probably be able to go in tomorrow morning.

I will feed you plenty of Lunar New Year food.

You can freely go out during the trip.

Since Qing was not a disciple of Kunlun, he could not be forced to do so, and he could not be punished severely.

So, from the Qing's perspective, there's nothing special about it.

I thought that I could use this opportunity to practice the secret method that Strange Monk had lent me.

If you have the skills, you can learn it in a few days without having to resort to the dirty, messy brainwashing training methods.

After leaving Jangmunjeon, she went to visit the infirmary.

He healed his own severed arm, so his bravery was commendable.

He was a monster with a poor prognosis, with boils on his face, a fever, and a pale complexion.

Still, he held out without complaining even once until he reached the Kunlun School, so should we call him a tough old man? Or should we say that he was worthy of the nickname of a monster monk?

"Happy New Year to you too, Yumomahop."

"Huh. It's not New Year's Day in this uncivilized Zhongyuan. It's the middle of a cold winter. How can it be New Year's Day? It's morning after midnight? Such uncivilized, ignorant nonsense."

"Can you just speak in Xizang?"

"[How can you say the New Year has dawned when winter is still deep? Just as the moon sets and the sun rises before the morning, the year begins only when winter passes and spring arrives.]"

"The Xijang calendar starts in spring, right? No, but why is your Xizang so perfectly fine, but your Zhongyuan is so broken?"

"[This monk possesses a deeper understanding of Zhongyuan language than you Zhongyuan people. My Chinese was so sophisticated that you Zhongyuan people find it difficult. I don't even know their language properly. It's truly a pity.]"

Qing was speechless.

He revealed that his level of Chinese language proficiency was very high.

"Huh? What did you say?"

"[It's natural for beginners to fail to understand the techniques of a master. The same goes for language, so they can't help but be unable to properly grasp the elegant Chinese of the original monk. Aren't you also a master of language, fluent in the Xizang language, which is sixty-seven times better than Chinese? You must understand how frustrating the ignorance of those beings is.]"

The strange tone was meant to be a result of his own attempt to show off.

Qing was wondering what to do with that, but it doesn't matter, right?

"Hmm. You're not wrong. Those ordinary people are just so frustrating. Sometimes, it really drives me nuts."

"[This is the pain you must endure. After all, the dull and incompetent mortals cannot expect to properly understand the vocabulary of geniuses like us. Please understand.]"

"There's nothing I can do. It's the fate of a master."

"[Excellent. Even if living beings are frustrated and unable to understand, would the Buddha be angry? The Buddha, with his great compassion, embraces living beings as if caring for a child. As a person of integrity, you too should always keep this in mind.]"

"Hmm. I'm having a hard time adjusting."

\textit{If he just speak in Xizang, doesn't he spoke like a normal monk?}

\textit{Why is this guy sounds cool?}

Even in my hometown, weren't there a lot of people with terrible mental illnesses who thought they were cool just by being different from others or by doing things that others didn't do?

But how about interpreting it positively?

It must have been Amukhaprap who thought he had stopped by Zhongyuan on behalf of the West.

So, it could be an attempt to show off in a cool way and raise the status of the entire group.

Well, I don't know about that, but I might just be intoxicated by the image (imagination) of myself speaking a foreign language fluently.

"Anyway, I heard the story. Elder said you'll take the blame for the hanging and the human shield. You didn't have to do that."

"[In the past, Buddha's disciple, Juriban-teuk, was known as the world's greatest fool. Even when he did something foolish, people didn't think it was unusual. It's natural for a fool to do something foolish.]"

Juribanteuk was a disciple of Shakyamuni, a legendary fool who achieved liberation while sweeping the yard and became an arhat (one who has broken the cycle of reincarnation).

Didn't they say that you can't memorize a sentence with four words in it?

Hehehe, Buddha said to sweep the yard.

I'm writing this in the special yard! I'm writing it cleanly!

The yard of the Jooriban Special has been completely swept clean!

Even the troubles of the mind were swept away cleanly!

So this was the principle.

"[Similarly, since this monk is originall known as a strange monk and a very eccentric person, the world would not consider it special if he acted cruelly out of a momentary whim.]"

It's like saying, "What if I add another notoriety to a body I've already thrown away?"

"Is that okay?"

"[In fact, your unparalleled cruelty is a sight that pleased me deeply. They were subhuman demons who murdered not only the villagers, but also the monks of the Blood Thunder Temple, and even their families, whom they called family in Zhongyuan language, sharing a single plate of jjamppong. The disciples of the main temple must have looked on with a pleased smile before the Reincarnation Gate. They did so simply because they are truly admiring and grateful to you.]"

"Hey, what? I just did it because I liked it."

It was when Qing smiled proudly.

"[However, as a Buddhist monk, and even as a senior monk, I say this. This is truly harmful. I urge my junior to never do such a thing again.]"

"What? But Yumomahop said it's a good thing?"

"[Having already lost his disciples, who were like family to them, to their hands, he wouldn't mind being torn to pieces, pickled, and eaten as a side dish. But what about the people of Cheonjun? What if those foolish beings think it's okay to abuse sinners and enjoy watching them?]"

"oh."

"[Punishing criminals is both just and savage. However, justice must not become a game or a pastime.]"

If that cruel justice brings pleasure to living beings, justice will seek out and torment sinners for the sake of pleasure alone.

It's a problem if there were innocent people, but wouldn't it be a bigger problem if there aren't any?

At first, you'll enjoy finding and killing those who were truly human, but then?

Gradually, the threshold of the sinner will become lighter and the crimes that can be played with and tormented to their heart's content will become lighter. If this continues, people will be hung, burned, beaten, and toyed with just for stealing a coin or two.

Just like back in the day when Jin-ssi and the witch Dal-gi used to kill people and drink alcohol to the tune of their screams.

Just like when Tibetan monks in the past would gouge out the eyes of commoners simply for looking at them insolently.

"[Moreover, living beings are foolish and pitiful beings who, once intoxicated by something bad, become addicted. Since you have entered the Buddha's path, you must not forget that these beings are foolish and stupid, and that they are therefore beings who must be cared for.]"

"Huh. When did I get into Buddhism?"

"[You have already obtained the affinity of the Thousand-Armed Tathagata and have mastered the great Thousand-Armed Tathagata. Above all, you have inherited the teachings of the enlightened Vairochana Buddha. If you are not a Buddhist, then who is? I bestow upon you the name of my Buddhist disciple, Panyasi-Nal. Panyana-Nala, what a wonderful name.]"

Qing's linguistic ability was absolute. He immediately understood what Panyashi Naal meant, and it was the exact same thing he had said before. Wise cow.

"No, who would have thought that you couldn't give up on that in the first place?"

"[In the Chinese language, it was called Guan-sa or Wu-yul, hmm, Guan-yu. It is too dignified for a woman, so calling her Wu-yul is perfect.]"

Qing decided to just say nothing.

Strange Monk was called a Strange Monk for a reason.

Even if I tell you, you won't listen anyway.

"[Panyana, you have avenged the enemy of this monk, so you are a benefactor to me personally. However, you may not have known it, but I have caused many harm in the cities of Zhongyuan, so I deserve to be severely reprimanded and scolded.]"

"It would have been fine if it had been a city in Zhongyuan."

"[So, the monk's infamy isn't just for you, Panyana. I am qualified to punish and condemn those filthy monks, worse than beasts. If it were something I did, even the foolish and ignorant of the heavenly tribes would not dare to imitate it. Therefore, it is the monk's duty to shoulder the burden, and you, Panyana, have no reason to be grateful to me.]"

"That damn panya nya, no, panya nya, no, isn't that a bit hard to pronounce? And, um, I want to eat panana. Do you think there's any in Yunnan?"

As if the Strange Monk was looking at a Strange Woman.

It was a gaze she didn't want to receive from Amukharap, so the tendons on Qing's forehead flared up.

"Ah. Okay. Get some rest. Oh, by the way, what did you decide to do about the Arab Grandma's Disguise?"

For some reason, it ended up being a temple that didn't trust old women, but Amukhaprap didn't care if Zhongyuan language was slightly different.

"[If it were up to me, I would rush in and slaughter all those devilish filthy bastards, but as you, Panyana, wished, I have decided to give the people of Zhongyuan the opportunity to help the Venerable and accumulate virtue.]"

"I thought about it carefully."

There was no need to point out each and every one of them, so I just said, "Okay, that's how it is."

I guess this was how fish cakes were supposed to be.

If there were no fish cakes in the first place, it would be difficult for the elders to attack the Blood Thunder Demon at will.

So, it was not entirely wrong to say that it gives you a chance to help.

At the request of the monster, he conspired with foreign powers to kill his disciples and annihilate innocent people, and he was punished for this.

We first attacked and eliminated the Blood Thunder Demon, who had dared to plot an evil and dangerous invasion of Zhongyuan.

The difference between these two was so huge that it would be a headache to make excuses like, "I cleaned it up first because it was an eyesore."

Aren't people just beings that I believe in because I want to believe in them?

This was a truth that Qing had painfully realized while suffering from the demonic seekers who were looking for the magic absorption technique.

This was also the reason why Amukhaprap keeps calling sentient beings foolish, uncivilized, retarded, and immature, and speaks of beating down sentient beings as if it were a natural fact.

Anyway, that's what it is.

I thought that if I went into the Repentance Hall and spent the remaining Lunar New Year holidays, Master might come.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

This was what Qing thought of the Repentance Hall.

It was stuffy and stuffy inside a narrow room, with only one small window cut into the ceiling, high above my head.

And a punishment room where someone who has done something wrong can go in and practice wall-to-wall meditation, staring at the wall for some time to reflect? The word "punishment room" was a bit harsh.

Ah, so that's why it's Repentance Hall.

A cave of repentance. A room of reflection.

There was no Repentance Hall in the Divine Maiden Sect.

Well, it's the sanctuary of Geumnam, a mysterious sect hidden in the mountains.

Qing has no common sense.

Well, that's because it's blue.

These were just some of the things I have seen and experienced, or what Ximen Surin has instilled in me with the heart of a true teacher.

So, even though it's a bit stuffy, I guess I'll do some serious training after a long time. I have to read the secret book, but it won't be too dark, right?

Qing thinks it's just a reading room.

Moreover, he said that he would not let her down with Lunar New Year food and that she could come out if she needed anything, so Qing took it very lightly.

Was that so?

Is there something wrong with the atmosphere?

Doesn't it look a bit like a prison?

Yes, Repentace Hall was a prison.

Usually a disciple who has committed a serious crime, such as the destruction of a knight.

This included traitors who harmed their masters and disciples, or sold the honor of the sect for personal gain.

And the villains who were declared as public figures in the martial arts world.

It was a prison where those who had committed serious crimes, such as those who had caused great damage to the sect or region, were imprisoned.

Although it was not an officially licensed brain prison in the country, in reality, even the government would quietly hand over to the local big sect when they caught a big shot like a famous madu that they couldn't touch.

This was Inviolable Agreement!

Let the martial artists take care of it among themselves!

We were not passing it on because we were afraid of the consequences or because it was a hassle!

This was the custom, and custom must be respected!

The fact that Jangmun Zhenren ordered the five-day repentance was a much more serious and dangerous rebuke than Qing had thought.

Ah. So even the true master Cheonbija was very serious.

I also thought you were telling me to go to the reading room and quietly collect my thoughts.

Well, then there's nothing I can do.

That doesn't mean that Qing was shocked or anything.

In the first place, why wouldn't Qing, who sleeps well on the street with a mat as a cover, go to prison?

You can come out and get some fresh air whenever you want, and they also give you plenty of delicious Lunar New Year food.

Even so, the reading room was only transformed into a prison experience.
