\chapter{My Prison Experience (11)}

The inside of Qing's danjeon dantian peaceful today as well.

The Taoist and Buddhist Qis who have taken good spots laughed and played, swirled and tangled together.

On one side, around the Ice Crustal that was placed on the ground, four or so Han-eum-han Jin-gi and the Ice King were gathered without any regard for their duties, wearing thick fur coats and enjoying the coolness.

I have no idea why they wore such thick clothes and gathered next to the ice rink.

But the original ice ball itself was a nonsense that was completely incomprehensible and difficult to learn, so the Jinkis were also like that.

At that moment, the door to the dantian bursts open and a group of demons rush in, panting.

There was a lot of honey on the back of the head, the hair was caught and shaken, and the clothes were torn and crumpled, making a mess.

But since it happens all the time, there's no need to worry about it.

Because finally, the Blissful Maiden True Qi platoon leader came in, closing the door with a bright expression on his face as if he was very relieved.

Today too, Blissful Maiden True Qi was having a blast, tearing, scratching, and beating the magicians.

After circling around once, she catched her breath and go to the warm, sunny spot, lie down with her head on the thigh of Mansang Yeo Ilgi, who was sitting cross-legged and meditating.

Mansangyeo Ilgi tilts her head in confusion, but didn't not stop her otherwise.

Is it because both of them were true spirits with the image of one and the same?

The Demonic Qis felt sad when they saw that sight.

Those Qis were not even from the same root, but they were so close together that it was a sight to behold.

What about the Demonic Qis?

When Blissful Maiden True Qi tried to run around, it was the beginning of a battle of wits, with Demonic Qis pushing each other by saying, 'You go to the Great Circulation'.

At least the golden headband bike and blood demon king's divine power, which were like the queen's older sister's, were pretending not to know.

In the end, won't the lower-ranking ones be the ones who were always grabbed by the hair, squeezed, and forced to run around the blood vessels?

So, if only they could have a purple, really strong eldest sister, they would have no more wishes.

They wish there was just one strong adult who could stop that Blissful Maiden True Qi's evil deeds.

That was when.

The entrance to the dantian opens wide again.

As the gazes of the people with unparalleled longing were focused on the entrance to the dantian, Chokomi, dressed in a new outfit, strode inside.

It was a wild outfit with a hood.

The magicians all jumped up and clenched their fists!

Look at that! They're really on our side!

Ho-Yeom Jin-gi was embarrassed.

Why was my dantian full of true energy?

On one hand, there were cheers and shining eyes, while on the other hand, there were displeased looks flying around.

however?

A blue headband was on Ho-Yeom Jin-Gi's head as he turns his head at the unfamiliar scenery.

The magicians' cheers suddenly cease.

What, it's blue? Blue?

The magicians who had been welcoming her stick out their lips with a tired expression.

The phobia was just embarrassing.

Flame hole. Blue border.

It was a martial art commonly learned in Sapa. It was a martial art that was (roughly created) spread by the first person in Sapa, who was called Ho-Yeom-Ma-Seon in the distant past, to increase the power of Sado-Ryeon.

It had the effect of stimulating the body's yang energy, but had the side effect of increasing blood flow.

Because of this, they tend to become impatient, angry over trivial things, and have a tendency to show off their sexuality.

That was why the miscellaneous sects classified as magic were very famous basic sects.

But it doesn't reach the level of a person changing, as the personality tends to become dirty.

Also, since there were many people who were familiar with it, it was classified as a magic technique, but it was not considered a true magic technique.

At that moment, another Jin-gi came rushing in, shoving my shoulder hard and saying, "Don't block the road."

A small, armored figure with a blunt expression thrusts into the dantian, making the sound of metal pieces clanking.

It was a thousand-mountain state, thousand-mountain true energy.

Cheonsan Taese, blue border.

It was a martial art learned by the armored soldiers of the military.

As it was common for soldiers who returned home in old age to take on minor military duties, it was one of the most common basic military duties.

The good thing was that the name was cool!

It has nothing to do with the Cheonsanpa.

Because it was a martial art created after seeing an animal called a pangolin.

There were no side effects, and it was claimed that the body becomes stronger and more powerful.

The reason for the claim was that it was not a meditation breathing method as was typical of military martial arts, but rather a breathing technique learned through military gymnastics.

Because the gymnastics was quite difficult, there were quite a few ronin who claimed that just doing gymnastics would train their bodies and improve their muscle strength.

Even though it was an unfamiliar landscape teeming with jinki, Cheonsan Jinki bluntly slithered across and lay down on a spot where there were no people.

A truly military appearance!

Because originally, soldiers were beings who would lie down anywhere and anytime they had even a little bit of free time.

As the still helpless Hoyeonmagi was fidgeting and looking around, two Jin-gis came into the entrance side by side again.

One was a little girl wearing a bright red uniform who made a cute, squeaking sound with every step she took.

But unlike the sound, the footprints left behind were made of bright red blood.

It was the result of an evil magic called Blood Cloud Magic and Blood Cloud Divine Art.

Right behind him was Chokomi, wearing a yellow uniform with sky blue cloud patterns embroidered all over it.

It was a martial art of the Hwangsan School called Cheonhaejingi and Cheonhaesimgong.

There was a reason why these two came in together.

"Huh? So your training method was bathing in blood? This was the absolute worst of the worst. That's why I'm stuck like this."

"Blood was the essence of human life. Wouldn't it be natural that if one absorbs that essence, one will be able to rule the world?"

But the man remained calm.

He was the one that the Qing call a cannibal.

Well, I guess I'll be here if I catch one or two.

He drew blood to train in martial arts, so he set up an inn on a remote mountainside, put poison in the food, and while he was sleeping, he sprayed poison smoke and ate the entire inn to death.

Since it was a remote place and there was nothing to eat, he ate the byproducts as a side dish, and he got sick of them so much that he developed recipes in all sorts of ways and even wrote a book about them.

The Blood Cloud God was golden.

According to his claim, it was very, very difficult to obtain training materials that do not have the side effects of evil magic.

It was a moment when one of the questions that Qing had had for a long time was resolved.

Even if the martial arts themselves don't have any side effects that can harm people, if the process of learning them was evil, it was considered a form of magic.

I used to wonder why that was magic.

Look at this cannibal bastard right now.

Since he saw people as training materials rather than people, wasn't he a brat who collected materials for his own training and then cooked three meals a day with the leftover materials?

Of course, this does not apply to Qing.

If you don't have to use evil methods, then isn't it not true magic?

It was a time when Qing would serve food as much as the gold border.

"I know of another divine skill. Are you interested?"

"It would be nice to have one more."

In this way, the internal energy method rolls in again with the principle of one plus one more.

But, that knot?

Doesn't it sound a bit strange when you hear it?

In addition to the teachings of Taoism, it was a study that borrows the imagery of Gongsun Xianyuan and, as if painting with ink, was very rich in the scent of ink.

No matter how many times I hear this, I feel like it's an authentic Taoist martial art.

This was not the kind of trick that a guy who was just talking about how to easily drain people's blood would come up with.

Soon, the martial arts window began to shine, the Heavenly Sea Deep Sky, red.

I think I've heard this somewhere.

Where have you heard that?

"This was the Cheonhaesimgong. It's the famous Hwangsanpa's divine technique."

That's right. The Heavenly Way. I think Master mentioned it in passing at least once.

In addition to the old school, he said that we should know the martial arts of the older schools, at least by name.

"Huh? Huangshanpa? You're a Huangshanpa? You're talking about the Huangshanpa in Anhui, right?"

The Hwangsanpa was an orthodox Taoist.

It was closer to a group of real Taoist priests who were more famous for their Taoist teachings than for their martial arts school.

"That was once the case. Huh, those dirty kids who were two different things inside and out. That's why I came out on my own two feet."

"The outside and the inside were different?"

"I was once the greatest warrior in the Hwangsan faction. This isn't about me bragging, but I've heard that no one in history has ever possessed the same talent as I do. But they never bothered to teach me their new skills. They taught those far less talented than me. Why? It's all because of my humble origins—"

"Huh. What."

Qing snorts.

"Why would you teach a guy who ate people every meal and ended up in a prison cell? You just assumed he was a spoiled brat and ignored him. In the end, the Hwangsan faction was right."

The cannibal's expression suddenly distorts.

And then he lets out a cry full of resentment in a trembling voice.

"You, what do you know, I, I……"

The cannibal tells his story.

A cheap prostitute who was once a member of the Hwangsanpa.

The woman came carrying a child, claiming that he was the son of a disciple of the Hwangsanpa sect, then vomited blood and died.

The son of a prostitute who had fallen into the sulfuric acid trap realized that the unfair treatment he had received was due to his dirty bloodline.

So the cannibals came out of the sulfuric acid group.

And I swear, I will make everyone in Hwangsan regret it.

Since you ignored this heaven-sent genius and did not teach him his divine skills, I will create a divine skill that was even more outstanding than his and prove my worth.

And then, the Hwangsanpa bastards will also lament that they lost the opportunity to become the best sect in the world by driving out the genius sent from heaven.

"So you were kicked out, after all. Didn't you just say you were kicked out?"

"I guess I misheard. Ahem. Anyway."

Thus, I created a new internal energy method that absorbed the sea of ​​clouds hanging from the waist of Hwangsan, the Cheonhaesimgong.

Even if you say clouds, they were just a part of nature and just damp moisture. It would be much faster to absorb human life itself and all of it!

It was the birth of the Blood Cloud God.

He was a cannibal who reused red martial arts and turned them into golden martial arts.

And that too was only a mid-late stage of the military at the time.

It seems that the saying that he was a genius sent from heaven and that there was no such record in the history of the Hwangsan faction was not a lie.

But to hear it from Qing.

In the first place, wouldn't he be such a bastard to come up with the idea of ​​sucking blood instead of clouds?

I wonder if even the Hwangsan faction recognized this burst of humanity and rejected it.

Anyway.

It was called Qingchuloram Qingoram, and this derivative energy, more powerful than the original, entered the dantian together with the original.

As they were from the same Taoist family, Joo Yang Jin Ki and Hwan Hee Jin Ki each grabbed Cheon Hae Jin Ki's hands and led him to a good place.

The magicians, who were very excited about the appearance of the golden-rimmed magician, clamor for the blood magician to come quickly and make room for him.

Looking at that sight, Ho-Yeom-Ma-Gi was sad.

As it was left alone in the doorway with no one to welcome it, teardrops hung from the axe eyes, a characteristic of the explosive attack series, and only grew in size.

That was when.

Bam!

They say that when you want to cry, you hit your cheek, and the straight-faced leader hits the crown of the tiger's head.

A hot horse rolling on the floor.

Above it, a shadow of a misty mist blooming somehow falls.

The attention of the Jinkis was drawn to the sudden, refreshing sound of a blow.

A small, evil smile that revealed sharp teeth and looked down at the crouching demon holding its head.

The background was painted with blood and dried blood all over the white uniform.

For some reason, a thick shadow was cast on the face, as if a thick line has been drawn left and right, regardless of the angle.

And inside that dark complexion, in those tiny, bean-sized eyes, a fierce light constantly flashes.

The Taoist and Buddhist jin-gis who had been snickering while saying they were having a good time all raised their eyebrows sharply, their expressions becoming serious.

While the magicians who had been muttering that it was good all swallowed their saliva.

The ten greatest magicians in the world, the Gwangyochusalganggi.

Descending into the dantian.