\chapter{My Prison Experience (1)}

On New Year's Eve, the lowest moon of the year, called Chuxi\footnote{除夕}, takes its place in the middle of the sky.

Some have described the last day of the month as the most pitiful and alluring.

A pale moon with only a faint blue glow remaining.

The pity of an existence that will soon disappear in a shabby state.

But today is an exception.

Because it is a day when everyone looks up at the waning moon with their necks stretched out.

Fight… …!

Soon, fireworks burst into the distant sky.

It was a rare sight to see the palace directly bestowing favors on the common people, so wouldn't it be like expensive gunpowder burning in the air?

It wouldn't be wrong to say that your taxes are on fire.

In any case, fireworks using gunpowder can only be seen if you obtain permission from the government and purchase expensive fireworks, or if you have them set off directly by the government office on New Year's Eve.

It was also the end of the year and the beginning of the new year, guaranteed by the palace.

"Happy New Year and may all your wishes come true!"

"Happy New Year, good health, peace in all things!"

"Happy New Year, may you be healthy, achieve all your wishes, and find peace!"

"Hongbao Na Lai, Hongbao Na Lai\footnote{紅包拿來}!"

Hongpo Na Lai is a phrase that means to ask for a red pouch, and if we were to use the language of the Qing hometown, it would be an expression that means it is time to settle accounts.

Because giving New Year's money is a custom that is still valid in Zhongyuan.

Deeng…! The bell rings on the ground.

There was a bang in the sky, the sound of fireworks exploding.

The bright lights of Seonyeong can be seen below the foothills of Ilwolsan Mountain.

Numerous temples ring their bells and large fireworks burst into the sky, signaling the start of the Lunar New Year, the greatest festival in Zhongyuan.

Year 6. Start.

\textit{It's a bit ambiguous since it was spring when I first fell into this primitive ancient Zhongyuan, but when counting age, I roughly use the New Year as the standard.}

\textit{Now, even though it's a vague memory, it seems like the workplace before I left was like that too, so whether I started in January or December, they treated me like that.}

\textit{Isn't that right? That doesn't make sense.}

\textit{Even so, it couldn't have been that bad, right?}

\textit{I don't even remember it anymore…}

"Xiao-mei, Happy New Year!"

"I've received a lot of love and affection. This year, Yi-mei will also rise your realm."

"Yeah. But I don't know…"

"Don't think too hard about it."

"Hmm. How was Xiao-mei enlightenment? Why don't you just tell me what it was like? My nephew and Elder Cui won't say anything."

"Listening to other people's enlightenment will only be a nuisance rather than helpful."

Jian Buxi's expression was unusually sullen, and it was not an expression of understanding at all.

"May San receive many blessings. Hmm. It seems a bit unscrupulous to ask San reaching Unrestrained Realm. How could some ordinary person reach Unrestrained Realm in a single year? Unless it's some absurd, timeless talent, gifted by heaven—or rather, created by heaven's mistake. Hmm. At least try to diligently reach the Midle-Stage Transcendet."

"Content aside, why are you so casually saying rude things?"

"Is it because I'm more of an expert? No. 'More' doesn't seem appropriate. I'm the only expert."

"Huh. I guess I just have to get rid of that sullen personality for the New Year."

"What? Getting square vs. becoming a bottom? Of course it’s the former right?”

A pretty face sneaked in between.

Xue-i-ri was just a pretty girl with a pretty face.

"Young Lady Ximen. Happy New Year."

"Then. This time too. This year, Iri. Hmm. Hmm. Okay. Stay healthy. Our Iri just needs to be healthy and strong. What's the big deal about cultivation and martial arts? Right?"

"No, I will become an expert."

"No. I just want you to be healthy. I don't expect you to be a master. People have a sense of shame. It's so admirable of you to have all your limbs intact, your eyes, nose, and mouth in place. It's so admirable that I'm almost moved to tears."

"This year, it will definitely reach Transcendent Realm."

"Hmm. Just that? You don't usually set your goals that low for the year, do you? You're going to reach Transcendent Realm this year? Do people have goals like, 'This year, I'll definitely breathe', or 'This year, I'll definitely walk without crawling'?"

"Thats's too much."

She suddenly turned her body around.

"Where are you going?"

"I'm going to practice."

"No, what kind of training is training right at the start of the new year? It's always the kids who are lacking who study when others are resting and play when others are studying. Come here. Come here. Let's go around and say hello and get some envelopes together."

Qing spread her arms.

Xue-i-ri looked at Qing with a faint expression, clearly conflicted in Qing's interpretation, and in the end, without even wiping a single wrinkle from her forehead.

Xue-i-ri hugged Qing's arms with a displeased expression.

Because it keeps happening like this, Qing is very excited and is teasing him by giving him medicine.

What can I do? Human relationships are inherently difficult to be equal, so it's inevitable that the person who feels uneasy will have to give in.

"Okay, I know you're all tired, but let's say hello to the elders and then go to sleep."

There are friends all around, and the Kunlun Taoist priests are laughing brightly and chatting.

Below the mountain, fireworks are splendid on the ground and in the sky.

It was worth running all the way to Kunlun Sect.

In fact, there was no reason to rush and go to extreme lengths to celebrate the passing of New Year's Eve.

But?

There is even less reason to celebrate a good holiday on the street.

So, even if I'm a little tired, if I can participate and share in the fun, what's there not to be done?

Even having to run with a stretcher carrying a crippled and decomposing Amukhapswa, his comrades, except for Qing, who was still in good health, were said to have been overdoing it.

He was out of breath, sweating profusely under his thick fur coat, and he even took off his hat and face covering, looking like he was going to die.

It was about two hours after sunset when we arrived at Kunlun Sect.

But after finishing the bath, didn't everyone have a smile on their face to welcome the New Year?

Sometimes you have to push yourself, you can't always be relaxed.

If others heard this, they would criticize her, saying that when it comes to overdoing something, she has never done anything wrong before, and that life itself is overdoing something.

"Okay, let's go and greet the elders."

Qingi Bomu also climbs Ilwolbong with confidence.

Qing is originally sensitive to the atmosphere.

As everyone was excited about the New Year, I was also excited, and I found myself humming along to a popular song that was several hundred years old.

I greeted the elders, and since I'm already rich, I don't really want a red envelope, but really, I guess that's what I get for making money.

Aren't all the so-called fortunes and good words given out of affection?

However?

"Youngest Sister, please reflect in the Repentance Hall."

"Oh. Me?"

"Youngest Sister. No matter how vicious and evil the opponent may be, there is a minimum standard that must be observed. Just how vicious is this disciple of the Taoist school's hands?"

Far from receiving any money, all she got was a scolding telling her to go to the Repentance Hall and reflect on her actions.

"This time, fortunately, the Strange Monk said he would shoulder everything on yoour behalf, and he said that it was all done under his orders."

"Oh, Yumo-, I mean, the Strange Monk?"

"Yes. He said wouldn't it be far better for him, already old, to be cursed than for you, in your prime, to be scorned? He's already known for his eccentricities, so it wouldn't be surprising to hear that, but isn't it a great favor all the same? I'm truly grateful to him."

"Um. He didn't have to do that."

"I thought Youngest Sister was mature and dignified, but you're still a childish girl. Well, you're only twenty-one, no, twenty-two. Huh, I always forgot about that."

Qing's eyebrows dropped at the scolding.

She was a peerless beauty who was competing for the title of the most beautiful woman in the world, so any man that looked at this heartbroken expression would in 10,000 out 10,000 times forgive her in an instant and immediately let go of his anger.

"Youngest Sister. It was absolutely not an example of what a Taoist master should look like."

But Chen Feizi Zhenren did not waver.

To be honest, he was momentarily shaken by the crying face of the Youngest Sister, who was like a granddaughter to him, and his heart momentarily weakened.

But he persevered!

When you need to scold someone, you need to scold them. If you ignored them because they where cute, it would became a bad habit.

"But, they deserved it…"

"It's not that I don't understand Youngest Sister's feelings. Even so, it was inappropriate behavior. It's even more so when it's shown in front of others."

"They were the ones who massacred innocent civilians purely for their own amusement. The number must easily have exceeded dozens. What about the resentment of those who died? Aren't they the ones who deserved to die the most painful deaths?"

"Hahh… Your hatred is so deep."

An ominous color slowly bloomed from the pupils.

The thousand-year-old monk said, 'Oh, the Heavenly Venerable,' and left the temple.

"How can life be so profound? No, it isn't."

The common man quickly hid his internal remark.

\textit{They say that like a teacher, like a student. I thought I was so envious of her teacher because I only knew how kind and gentle the disciple was.}

\textit{I realized that the relationships in this world are not indifferent, but that the relationships that were meant to be met eventually did.}

"It's true that they deserve to die a painful death. But that wasn't the kind of thing to show to the world. If everyone in the world thought that way and became cruel, what would the world become?"

"Then wouldn't they be afraid and not do bad things?"

"No, on the contrary, it only shed great blood in the world. Besides, aren't human affairs imperfect and our perceptions all different? If we were to torture and kill those who are considered evil, wouldn't there be innocent people who would suffer such terrible pain?"

"Then wouldn't it be okay for those who turn out to be truly evil? It was the same this time."

"So, just how far can a sin go to become truly horrific? Since the human heart is inherently treacherous, even a small misfortune for oneself or one's family will inevitably lead to a great resentment. Therefore, if such hatred grows, it is said that a cruel era like the Spring and Autumn Period and the Ten Kingdoms Period will arrive."

"That…"

Qing's beautiful lips tremble.

A more primitive and ancient era than today.

Regardless of East or West, there was an era of just revenge that Qing spoke of.

It was a barbarism that was truly a bloody chain of bloodshed, where revenge was considered a legitimate right and suffering for evil was considered a duty.

That's why it was an uncivilized era.

Even in the famous Hammurabi Code from three thousand years ago, the phrase 'an eye for an eye, a blood for a blood' or, in the words of the learned, 'the principle of equal retaliation' was a measure to prevent such barbarism.

If you lose your eyes, just take away your opponent's eyes.

If you shed blood, receive only the same amount of blood.

This was not a society that encouraged revenge, telling people to take revenge in kind, nor was it a recommended law that encouraged people to try revenge.

It was an attempt to break the chain of endless cruelty in the name of revenge by establishing a law.

But that didn't convince Qing.

\textit{Death to death?}

\textit{But what if he's caused multiple deaths?}

\textit{Are we supposed to just let those fucking bastards die in peace?}

\textit{I can't admit that. No, I won't.}

\textit{And whether he's really a bad guy or not, that doesn't concern me.}

\textit{Wouldn't it be possible to clearly determine this by using the Evil Karma numbers as an aid?}

Of course, it wasn't just her inner feelings.

Qing's expression was so sullen that anyone could tell that she was not reflecting at all.

"Was the tragedy of that village such a great wound to you? This is it. Hatred is etched into your heart like that."

"It's more hurtful to me that those bastards, or rather, those beasts, are alive and breathing. Should we even consider them humans? They deserved it. Rather, they probably still lived a day or two before they died, so isn't that an undeserved reward?"

The sage shook his head at her.

"I'm not criticizing your decision to punish the wicked. Your determination to uphold justice through the wicked's cruel fate is certainly admirable."

And then, the celestial maiden smiled strangely.

"So, I command you to undergo five days of repentance. Although I am not an Elder of your sect, if Youngest Sister truly see this old man as your Martial Brother, will you please do so?"

What else she could say?

Qing had no choice but to say, 'Yes'.
