\chapter{Let's Kill the Bandits (7)}

"Well, do you know each other?"

Amukhaprap was impressed by him.

"This unclean beast does not know himself."

Amukhaprap does not know the language skills of Qing.

Even though I could hear a word, even the people of Qinghai's Zhongyuan only occasionally understood it one by one.

Expensive! Bargain! Expensive! No! Expensive!

Or the back room! Quick! The back mountain! Urgent!

Of course, a doctor can understand, but just seeing a list of words like this doesn't mean you can say you know how to speak.

"Lies! Heh heh, you seduced a truly beautiful woman in Zhongyuan? were you thinking of starting a family now? You said the Western Lady was the most beautiful, so I guess you're a man after all?"

"Go! And you stupid brain! All the beauty of Zhongyuan people comes from the Tibetan bloodline, from the great ancestors of the Western Zhuang. Pure Han blood, it doesn't exist!"

Tibet was a country of the Western Zhang people that existed approximately a thousand years ago, and it achieved the feat of conquering Chang'an, the capital and center of Zhongyuan at the time.

It was the most powerful nation in the distant past, a nation that even Zhongyuan trembled and treated as an older brother.

Of course, Qing doesn't know anything about other countries' history.

"Heh heh, since we're already ruined, and our chief was in this state now, what's the point of saying that? Isn't that just plain dirty self-masturbation? Isn't that right, Master?"

"Huh."

"Master, I had a rough idea, but even so, I looked at the three blatant words that were hard to ignore.

"This vile seed, you act like a dog. You pretend to be friendly with the Great One, but you have no connection to my band of thieves. This beast, you present me with a delusion."

"It's not that dog, but, um, what did it teach you?"

"No, it's not. It's the great merit of the compassionate Buddha himself, who discovered a beggar in his past and gave him a Dharma name, taking him in, and saving his life."

"No, you needed a slave who would listen. Hey, do you know what this author names people? \#\#, or in the Chinese language, Galdolyudu—"

"conflict!"

Qing barely managed to suppress her laughter.

The character 'gal' refers to thick clothing and 'dol' means to protrude or convex.

"Sigh."

Honestly, I couldn't hold it in. The laughter overflowed and overflowed as the Strange Monk screamed, "Gal!" What should I do?

Qing opens her mouth with a slightly choked voice, a hint of laughter.

"What's the name? Doesn't that mean you saved someone from starvation? If I were you, I'd be grateful to someone who gave me food."

"You were a noble person. As expected, you were wise. Your penetration of truth was like that of a great monk who penetrates the fruit of the tree."

"Don't be ridiculous! He just needed a slave to work for him! He gave me a lowly Buddhist name and abandoned me, so if only he had taught me the basics of martial arts! He kept me from becoming a master by running errands until my bones hardened, blocking my chances! Didn't you even block Saritasa from teaching me the Vajra Sutra?"

They say that martial arts were better when learned at a young age.

Because it was the only time when one could train in martial arts and have one's frame change accordingly while one's bones were still soft, it was the only opportunity before the transformation.

Is there only external power there?

There, the child's upper, middle, and lower dantian channels were in good communication and the blood vessels were clean, so the speed of movement and output of the body itself increase significantly.

The common saying that it was difficult to achieve great things in martial arts after the age of twenty was precisely this.

"Hmm."

Even though he was a monk, he was actually a martial arts sect, and just like Shaolin Temple was closer to a sect than a temple, so you took him there and prevented him from learning martial arts?

Wasn't that a bit harsh?

Hey, Amukhaprap, tsk tsk.

"You shameless beast, how can you blame yourself? Your wretched life has been replaced by the Buddha's mercy. A sentient being who sheds tears while eating barley porridge, your expression instantly changed, you were a fraud. Before learning to fight, you should have studied the Buddhist scriptures and expressed gratitude to the splendid Vairocana Buddha. Instead, you were only interested in martial arts, so you blatantly blabbed about your resentment to all sides."

"Well, that's true too."

Listening to Amukhaprap's words, there was some truth to it.

I brought him to save a dying man, but he was completely uninterested in his Buddhist studies and duties as a monk, and he kept talking behind my back, saying that he simply didn't teach me martial arts.

Even if I were you, wouldn't you think that it would be a bad idea to teach martial arts to that young child?

"Even so, I shouldn't have stopped you! Because of you-"

"No matter how outstanding one's strength, if one's heart was evil, one will simply be born a demon. Foolish people who were greedy for immediate achievements but end up causing trouble later on end up creating beasts."

Why was this Strange Monk constantly talking nonsense?

However, I think he was a bit thick-faced when he comes out after being crazy about the magic of absorption.

If I do it, it's Buddha's will, but if someone else does it, it's evil greed? Surely this was why it's called evil karma?

Anyway, he was a truly cruel teacher, having taken him in and prevented him from learning martial arts.

"Even so, isn't trying to kill me by poisoning me a bit too much? They even tried to give me some weird, cow-like Buddhist name, but if Mr. Eomuk refused, he wouldn't be the type to hold a grudge or force it on me. Ultimately, isn't it just because he's greedy for Eomuk's martial arts that he took that name, "Cheol-Nipple," and now he's talking nonsense?"

"Ha. We're not communicating."

Then the bandit leader with the embarrassing name lies down on the floor.

If you're going to kill, kill quickly.

"Heh, how could a full-bellied woman understand? Wielding all sorts of powerful martial arts, she must have learned martial arts from a young age, building a foundation through beekeeping and learning them before reading. Do you even know what hunger is? And do you know the sorrow of being hungry because you have no strength?"

"You're funny. When I was getting spit on and beaten with sticks every day, barely able to eat bugs while being careful not to notice them, if someone had picked me up, I would have treated them like a benefactor, like a parent, for the rest of my life. You're just a worthless brat. Who do you blame?"

"What-"

"Enough. Without shame, you were a beast that can no longer be turned back. A small mistake or a shameful sin of your own greatness. The life you saved, you reap."

As Amukharap said this, he picked up the iron bar that the bandit leader had dropped and held it in his hand.

Then, Qing suddenly blocked the Amukhaprap with his back.

"You were a brave man, who has prevented the great murder of his own. You were even more brave, and the Buddha will bestow ten thousand points of merit upon you. But that was already a beast—"

"No, I'm not saying you shouldn't kill them. It's just weird. Oh, right. I don't know, because when I fought the bandits, all I did was cough up blood."

Qing kindly explains the situation.

What kind of thieves in the world deal in betting, even at the level of the Byeonggi Seonggang, were most of them mere second-rate, faded, luminous attachments, and were merely swordsmen.

Isn't this very suspicious?

Even looking at the bandits, more than half of them were from Zhongyuan. So, if we were to argue in a logical way, wouldn't they be in collusion with foreign powers?

Those guys must have some suspicious intentions if they're blocking the road in this rural area.

Amukhaprap's eyebrows arched sharply.

Fortunately, the bandit camp was full of food supplies.

Well, since there were a lot of people, wouldn't it be natural that there would be a lot of food?

So today, Qing was the captain.

Although I didn't learn to cook separately, I'm a master of eating who knows how adding flavor to flavor can have a synergistic effect.

It could be said that he had the talent to become famous and successful if he had been a monk rather than a monk.

But the kitchen in Jungwon also belongs to the man.

All the doctors in Zhongyuan were men, and no matter how excellent a woman's medical skills are, she was just a female doctor, not a doctor.

All the maids were men, and the women, no matter how amazing their cooking skills are, were just the head of the household or the mother of the kitchen.

A woman was someone who can cook rice but cannot cook. That was because she was a woman.

Ximen Surin's radical female-centered ideology did not emerge for nothing.

So, from the beginning, Qing was destined to never become a master, and it was not something to say to a true master who has achieved the greatest feat of the youngest Hwagyeong.

That was why, no matter how plausible the food that Qing makes is, it was not a dish, but a meal.

And in fact, Qingdo, to be exact, has not learned any cooking skills and was only good at cooking alone, so strictly speaking, it was not cooking but rather eating.

"I will help you."

"No. It'll be ready in no time. Want a taste? What kind of thieves have put together such a lavish display of ingredients? Thanks to them, this looks like a masterpiece."

"Yes. Okay. Hurry up."

Xue-i-ri scoops up the porridge bubbling in a large pot with a large wooden spatula and eats it in large portions without even letting it cool.

How can he eat the porridge as hot as boiling water without even blowing on it? It was truly a truly amazing performance by a peddler with great skill.

"Haa, huh, hot, hue, madik, madikteoyo. Mimi! Mimi! Hoot, hah, hue, hue."

First, put it in your mouth and blow on it to cool it down, and with the surprising and clearly visible dirty table manners, Xue-i-ri keeps saying it's delicious, Mimi (very delicious).

"Are you a little bored? How's your liver?"

"I'll try eating a little more."

And another big spoonful.

Ha, hot, ahh, a manly moan escapes, but since everyone hears it every time they eat hot porridge or soup, it's now just background noise that I don't even pay attention to.

"Sigh, gulp. Well, I'm not sure. I need to eat more."

"At this rate, I'm going to end up eating it all by myself."

Qing wraps a huge cauldron in a towel and flashes it.

When you come outside, there were three huge bonfires.

One was surrounded by a group of people, while the other two were surrounded by dying bandits, groaning and gasping for breath.

They were always noisy and demanding to be spared, so I chose the one with the highest level of evil deeds and grilled him over an open fire, and everyone became quiet.

"Do you really have to eat dinner here?"

"But, we have to keep an eye out, just in case one of them starts messing around. And above all, dinner was supposed to be eaten together, right? We can't just take turns keeping tabs. We have to eat together. Family doesn't know. Eating together was incredibly important, right?"

"I'm asking if you're being too relaxed. With the wounds melting, there were more than a few people who will soon be suffocated."

"Whether you freeze to death or bleed to death, that's the point. And what matters was the message, the meaning of your actions, right? We don't care whether you live or die. We don't care whether you die or not. That way, if you ask them anything, they'll answer obediently without even looking at their livers. They need to beg, not negotiate."

"Amazing! Amazing wisdom! You, my valiant one, weren't the contents of your head empty? It's the audacity of daring to deceive your own great self."

"That's not something a fish cake should say. How can you be such a master of the art of cooking and eat bread without even knowing it's poisoned?"

"You, as brave as you are, were indeed brainless. The purpose of almsgiving was not to benefit oneself, but to provide sentient beings with opportunities to accumulate virtue through offerings. Therefore, it was the fate of a Buddhist disciple to not be picky, even if it's poisonous. Even the Buddha Shakyamuni, the present-day Buddha, enjoyed eating the phlegm of others the most."

Qing was a Taoist monk, so of course he had to memorize basic Buddhist studies in addition to Taoist studies.

According to the actual precept, you should not refuse anything that was given as alms.

Of course, there were countless Buddhas and countless sects, so some temples keep them and some don't.

Of course, Qing scoffed.

"No, it's not that. I didn't want to share it, so I swallowed it without chewing. So, I don't know if it was poisoned, but I couldn't taste the sharp, sharp taste."

"Truth be told, it's thanks to the Great Self that you weren't poisoned. The Great Self collected all your venom."

"Well, that may be the case. But why do you keep giving people Buddhist names like that? Even I would be twisted."

"You were valiant, yet ignorant. The name Sakyamuni gave his son, Nahu, was the very name of a burden on the Indian horse. It was a severe derogatory term, meaning an obstacle to one's practice, an obstacle, a devilish child who clings to the afflictions of blood and kin. However, he was not ashamed of his name, and to avoid becoming a burden, he practiced secretly (secret practice). Thus, he eventually became the great master of the great Esoteric Buddhism."

As far as Qing knows, the name of Nahu, the son of Shakyamuni, was interpreted as a lament for the love for blood relatives that arose unconsciously rather than such malice, that is, a lament for the suffering.

"Seriously, you didn't say a word. It's more annoying when it's plausible."

"That was because the great self was invincible and never defeated by the glory of the Buddha."

"Okay. Just eat some porridge. Oh, by the way, didn't the Buddha over there tell you not to eat while you're here?"

"Your admirable memory was like a chicken's head? The great One has already spoken, eating all the offerings and bestowing virtue upon the Buddha's teachings."

It means that you shouldn't eat it, but you will eat it if given to you.

I don't want to give it to you, but.

No matter how much you hate someone, you shouldn't make them sad with food. This was Qing's firm belief.

The large bowl of porridge doesn't look very good, so I carefully examine the contents.

Qing's friends were all like that at first, but now? When Qing prepares a meal, they secretly drool in anticipation.

As expected.

The amuk haprap that I carefully took a bite of was making a fuss.

"Oh. Oh. Amazing taste. A dish so unappealing that even a dog would turn its head away. How can it be so delicious? You, noble soul, should immediately return to your hometown and take charge of the kitchen. Even Buddha would break his fast with such an evil taste!"
