\chapter{Let's Kill the Bandits (3)}

The night deepens, but the mountain was still there.

My stomach feels gurgling, so I'm hungry. My hunger has only grown as I've learned to love the raw and tender foods of the past.

Now that I look, I see a faint light shining down from somewhere below, halfway down the mountainside, over a cliff or a steep hill.

Of course, if you set up a camp, you would light a fire and be on guard.

Since I couldn't find it when it was bright, this was why there was space behind the pillar.

The space under the steps was wider than you might think, so of course it won't be visible from below.

If you can't see it from above, it's definitely an excellent geographical location for building a mountain fortress.

"I'm following because I'm going first. The process of determining whether you're a beast or a human, you Zhongyuan bastards, were chasing after me. Even a dog raised by the headquarters can easily slaughter a fleeing bug. In other words, this proves I'm inferior to you bastards."

"Huh, wait-"

It was Amukhaprap who jumped down with his body flying without giving Qing a chance to stop him.

"Guys, it might be a trap, so if anything happens, we'll retreat immediately. Let's not circle around for now, but watch from above. If anything seems suspicious, I'll carry you away. If anything looks off, just hug me. Got it?"

"Yes. I will hug you."

So the group jumps down a low cliff and runs down the slope.

Following the light that has already gone far ahead.

It was a fairly large campsite with five brick buildings and a thick tent that can accommodate up to ten people, depending on the season.

Qing just sticks his head out on top of a steep hill.

In the meantime, a monk falls down.

When you look at it from a Qing perspective, you may not know what the difference is, but from a Qing person's perspective, it looks like the hem of a lama's robe.

Men sitting around a large fire on a cold day suddenly jump up from their seats when they see a lama falling from the sky.

But as they stand face to face and silence flows, a deep wrinkle forms between Qing's eyebrows.

That kid, I knew he'd do that.

Qing was just about to give the signal to retreat.

As Amukhapal's mouth opens, a strange pronunciation flows out. It was not a Zhongyuan language, but that does not mean it was difficult to understand.

Qing's ears perk up, and he listens with his superhuman hearing.

"What was it? Aren't you the generals?"

"What was the matter with you, Monk? were you perhaps lost?"

"[Ahem. I came here because they said there was a gang of thieves, but I guess I've come to the wrong place.]"

The men exchanged glances at him.

"[Haha, we're currently developing a new village. Um, have you eaten yet? Would you be so kind as to allow us to offer you food?]"

Huh. The nonsense of the fish cake maker that suddenly passes by.

Seeing the men's attitudes, I wondered if it wasn't just empty talk, but the truth, like they had done me the honor of offering food.

Gulp.

Rather, I got hungry.

It seems that it was not a base for bandits, but rather a pioneer village established in a good location.

If you offer to treat him to a meal, surely that old man won't try to eat alone?

"I must subdue that band of vicious thieves as soon as possible. But how can a Buddhist deprive you of the opportunity to make offerings? Just give me a piece of gourd or something to devour."

"[Please wait a moment. I will bake it for you quickly.]"

"[Just a single, cooled piece would be enough. But aren't there any suspicious people around here?]"

No, that kid?

Bakre was a barley bread eaten by the westerners. It tastes similar to naan made with milk.

But a piece of bread?

Are you saying that you want to eat alone?

When you get here, there was no doubt or anything.

It's just that the fish cake soup was weird.

Well, I already knew about it, didn't I?

He's a quirky person, his speech was strange, his bad deeds were high, he's arrogant and obsessed with magic, but he has a secret monk-like side, so I don't think he'd plot something sinister.

This was the thought of a woman who was very suspicious.

If you insist on being heard, why not use the Chinese language to lower your guard and make it louder? Why would you insist on using the Chinese language to show that you were not a bandit?

And on top of that, I have to go find a thief?

In the middle of the night, not eating, not eating! Not eating! Starving yourself, how can someone starve? No matter how much you hate your enemy, you shouldn't break their rice bowl, so how can you kill someone?

"Well, let's get moving. If you stay up there and see Eomuk Samhap, he'll be upset that you didn't listen to him. He'll start talking nonsense."

The fish cake samhap was innocent.

But with a side of spicy sauce.

"Didn't I just tell you to be careful because I was suspicious?"

"That old monk over there said he wasn't a thief, so he thought, 'Oh, that's right,' and tried to search another mountain. We have to go and stop him and kill that thief."

"Do you know how to listen to the chief?"

"Huh? Yeah. Didn't I tell you?"

"I didn't do it."

"Because I didn't ask? No, San, you didn't even ask that. You're not that interested in me? How can you be like this to me? You don't even know what I like or what my hobbies are, San. How can you be so disinterested in my first friend, the first person I dated?"

"Huh. You like eating and have a hobby of eating, don't you?"

"Ah. As expected, it's a mountain. I knew it. I'm a little touched. Anyway, let's go."

It seemed that Eomuk Samhapdo was a bit lacking in people, that is, he was of the type with below average intelligence.

I had that kind of feeling.

Of course, that's not a big problem.

There were already a few people with low intelligence around me. There were three people in order of stupidity: Lee, Hee-mae, and Jang-myeong. So even if I add one more person to that, it's only going to be so-so.

But should I put the fish cake samhap uncle in front of me or behind him in front of my sister-in-law?

No, if you catch a thief and ask him, "Are you a thief?", what answer do you get?

"Yes, I am the thief. You have remarkable insight and observation skills. were you a detective? May I ask how you figured it out?"

What kind of polite response would you get?

Just say, "I'm not a thief."

If you ask a dumb person if they were dumb, they will get angry and say, "I'm smart."

Oh, how did you know, hehehe, where would someone act like an idiot?

As Qing was about to leave, a hand gently pulled at her sleeve.

It was Xue-i-ri.

"Miss Ximen. Which number am I?"

"Let's see. San-i, Zhuge-i, Hwangbo-hyung, and then there were the old men from the upper class whose names I don't know, one by one, two by three by four, and then Jang-myeong, and then the Master and the Divine Maiden Sect family members… Hmm, there must be between three and four hundred of them, right?"

"no, I do not want."

"If you don't like me, what can you do? Why would you go back in time to meet me? Come on, let's go."

So, before Qing A-muk-hap-rap notices, he quickly bypasses the mountain village.

Fortunately, it seemed to take some time to bake the bread. This gave them enough time to pretend not to notice and settle down at the bottom of the slope.

And soon, as the Amukhaps, which had emerged from the mountain, approached, the Strange Monk, who had noticed the head of a blue dragon suddenly popping up, stuffed the remaining bread into his mouth.

Everyone's eyes were rounded and crescent-shaped.

No, if someone saw me, they would think I was stealing it.

I actually intended to steal it.

No matter what, he didn't even ask me to try it once.

Well, this kind of gross gluttony was not surprising, since it occasionally existed even in my homeland.

"You said you'd eradicate the bandits, but why were you walking out so haphazardly? And do you think it tastes good if you eat it alone? It's going to make me sick."

"No, thieves. Good, gentlemen. They were the pioneers of the unknown."

"There were a lot of bandits around here. What kind of pioneer village was this? Those guys were bandits."

"Foolish you, they were the West Chapter. This was the most peace-loving and good-natured of the countless bloodlines in the three thousand worlds. From past to future, there was not a single West Chapter thief."

"Eomuk Samhap was not a Westerner, but some kind of Westerner? He left that bloody handprint, saying he would break my leg, but what about peace?"

"You, my brave soul, were once cursed as a demonic being. Gifting a great man to a demonic being who would suck the essence of all humanity proved my love for peace."

The expression on his face suddenly turned sour.

"No, even if you say so, it's like that. Anyway, those kids were thieves, so if you go and search, you'll find out where they've piled up their stolen goods."

"How dare you question the Chief! The Great One has already made his decision, and such outrage cannot be tolerated!"

"I'm not some kind of nationalist or anything. If you really don't like it, just wait here. I'll sneak in and check it out."

"That's right, okay."

Suddenly, the sound of a thick, sticky liquid gurgles, and blood flows out of the mouth.

"Fish cake? Why was it like this?"

"\#! \#\#! Ugh, ugh."

A prologue that pops out in the midst of chaos.

'Poison, addiction.' That was what Qing understood.

Amukhaprap shoves his gaunt fingers into his mouth, roughly spits out the barley bread he had eaten alone, and then immediately collapses to the floor.

Sitting cross-legged and expelling poison with energy.

"Miss, you're really being a bit sloppy. You ate it all by yourself, so gross."

"I knew this in advance. So, I will deal with your harmful poison. You, Lee Da-kyung, be patient. I will deal with the poison."

Just hold on for thirty minutes until the poison was expelled.

Heh. What the hell were you holding out for? If you're late, there's no killing to be done. I'll just kill them all.

All the thieves were gone.

My body was aching from lying down for so long, but now that I think about seeing blood after such a long time, my heart was pounding really fast.

"Hey, come here and hide some fish cakes somewhere safe. Do you know what I mean?"

"yes yes."

As Xue-i-ri lifts the Strange Monk and goes down the hill, Qing draws the Moonlight Sword and thrusts it out to the side.

When Jian Buxi untied the rope she was holding and removed the organ underneath the handle, bang!

The first volume of the Nanga Moonlight Sword appears.

The moment the sky brightened, countless torches were lit up on the hill.

"This damned rascal! He's hiding the party! Hurry up! We have to kill him before the Strange Monk exorcises the poison!"

It seems like a kind of motivation, but then doesn't that mean you're afraid of fish cake soup?

A ferocious smile spreads across Qing's face.

At first glance, there was one young beauty, one beauty who was not so young as to still have a childish look, somewhere between a girl and a woman, and one man wearing a hat.

They were easy opponents for thieves.

That was until I got it torn apart properly.

The blade of the Nanga Moonlight Sword was from right to left.

The long handle of the Nangabong draws a huge semicircle that a sword cannot originally have, so the bandits who were charging at the forefront were caught in its path.

The narrow downhill path where the thieves' mountain village was hidden, the blade dug into the thick thigh, the feeling of cutting through the firm, resistant muscles.

One, two, three, four, five! Six!

Yes! This was it!

It's the thrill of cutting down something that I had forgotten for a while.

A burning sensation that runs from the blade to the handle, from the handle to the spear, from the spear to the hand, and in an instant, passes through the nerves and reaches the danjeon, blooming brightly.

This indescribable pleasure, the heat burning up my spine and rising to my crown of my head.

Three thieves with lost legs roll down the slope, brushing past the group of Udangtang.

"Kang-gi! They were experts!"

"What!? There's only one expert here!?"

Qing'er burst out in laughter, but her smile adds to the ferocity.
