\chapter{Let's Kill the Bandits (6)}

A farce unfolded at the base of a bandit group, holding onto the gate of a railroad barrier.

The captain (presumably) who entered first tried to close the door, so the subordinates who followed him began to desperately try to stop him by holding onto the door and pushing it away.

As other thieves took advantage of the gap, the passage between the two doors began to narrow again.

It looks like the guys inside were helping close the door.

It seemed like he had absolutely no regard for loyalty.

Those who had taken refuge inside the fortress because of those who were blocking the door, wouldn't they now be closing the door once they're inside?

So, a few more thieves clung to the closing door and pushed it hard.

And those who went in tried to close the door.

Then, finally, after the fleeing people entered the fortress, some of the men who were pushing the door suddenly jumped inside.

The moment the balance between the opening and closing forces was broken, the thieves holding the door were hit by the door leaf and roll around outside the fortress.

Rolling around, he jumps up, looks at Qing, runs towards the door, and knocks urgently on it.

These were the majestic words of the thieves who held the door open, dedicating themselves more than anyone else to their comrades.

Meanwhile, Jian Buxi picks up a handkerchief and gently wipes Qing's face.

He was extremely cautious, fearing that it might hurt, but he quickly wiped Qing's bloody face with his perfectly familiar hand movements.

"Hmm. Sister-in-law, your face needs to be clean to be pretty."

"It's going to get dirty again anyway."

"Then just wipe it again."

Jian Buxi laughed, wringing out her handkerchief.

He expresses his surrender by spitting out all the blood that had dripped from his handkerchief due to his strong strength.

"Open this! Open it!"

"Open up, you little shits! Open up!"

On the other side, the voices of the thieves who were still banging on the door were incredibly urgent.

As Qing was watching blankly, he heard Paengdaesan's low, heart-pounding voice.

"Hmm. were you planning to leave it there?"

"I'm thinking about what to do. I could just go over there and slaughter them right away. Hmm. Well, I don't even know what's inside."

"You're so careful in times like these."

Paengdaesan nods.

Qing chuckles at him.

"Well, you can't get hit twice."

He had already had the experience of rushing straight into the enemy's base and getting beaten up, as the old man of the Blood Corps had risked his life to lure Qing into a trap at Mount Lao Shingajjimyo.

It seems that they let their guard down because they had never suffered any damage by rushing in before.

The experience of beating everyone to death and destroying them with hammers in Guangdong and the Green Forest incident was poisonous.

So, it looks like the thieves were just scared and hid in their visible mouse holes.

But, isn't it possible that there might be some kind of means or trap in the base?

"Hmm. If I set it on fire and burn it all down, it won't burn because it's made of bricks. It's a waste. Should I use the poison bullet Lan-ah gave me? How much food was in there? I can't just leave them to starve to death, can I?"

This was definitely not something that a person from the political party should say.

Peng Daesan Mountain makes an impression on him.

"They said a group of bandits kidnapped someone. There might be survivors."

"Well, then there's nothing we can do. There's a last resort. I didn't want to go this far."

"Is there any way?"

"Yi-mei, give me that, that."

"That? What was that?"

"Champa. I'm hungry."

Then, with a look of approval, Peng Daesan said,

Jjamppong was a dish eaten by the Westerners, and to put it in the Chinese style, it's called Byeokgokdan. They could be considered the same food, as it's made by mixing grain powder with honey.

It would be too dry and chewy to eat raw, but I was hungry anyway.

Qing wipes his hands on his pants and takes a bite, chewing it for a long time.

I want to stuff it into my mouth, but no matter how much it tastes, I'm not yet at the level of a good eater to swallow the dry, chewy wallflower.

Above all, I think there will be some delicious food in the thief's mountain village.

It's a shame to fill a meal with these substitutes. It's a waste. Hunger was a resource, after all. If you're going to eat, you should eat something delicious.

If someone heard this, they would be shocked.

But we must also understand Qing's feelings.

This was what happens when a person becomes obsessed with food.

"Miss Ximen."

"Oh, you came here? Come here, come here. Want some champagne too? Aren't you hungry?"

"Yes. Yes. Yes. I'm hungry."

First, the four of them grab a jjamppong each and slowly eat it to roughly fill their empty stomachs.

"So, what were you going to do?"

"Huh? I'm just going to stay like this. Oh, was it cold in the mountains? Should I light a fire?"

Then, as they wandered around peacefully gathering torches, Gyeonpohui and Xue-i-ri joined them and lit a fairly large bonfire.

Qing laughs and stretches out her white hand towards the campfire.

"Ah. It's warm. Being warm and not feeling cold were two different things, right?"

"yes that's right."

"Come closer to the mountain and light a fire. I'm already sensitive to the cold. You should've told me earlier. I'm not very sensitive to cold, so I wouldn't know if you didn't tell me."

"That's not it-"

"\#\#\#\# \#\#\# \#\#! \#\#! \#\#\#\#! \#\#\#\#! \#\# \#\#\#\#\#!!"

At that moment, a thick stream of profanity cut off Pang Dae-san's words.

From what I've heard, it was mainly a cry to kill all of the parents, especially the expressions of inappropriate affection between parents and children.

Then, a lantern jumped up and down, but only for a moment, and then it quickly passed the group by.

It was Amukhaprap, a Strange Monk who was resurrected from addiction.

Amukhaprap jumped over the wall in one breath - Ah, Kabi, it was a little short - unfortunately, it was about two feet short, so he threw the lantern with a bang and slammed his hand into the wall, and the sound of shouting, screaming, and hitting the wall echoed.

This was the last resort, the fish cake production.

Are you worried about the possible dangers of Jinji?

Well, wouldn't it be better if people who were willing to take risks take the lead?

It's okay if a temporary colleague who was eccentric and has high karma, especially one who has no loyalty and eats bread alone, abandons camaraderie, was a bit dangerous.

It's a bit of a petty thought, though.

But, when it comes to being with colleagues, isn't it always Qing who takes the lead as someone who was 'worth taking risks'?

So, Qingdo may have the right to put someone ahead sometimes.

Also, Amukhaprap has the right to take revenge.

"Sani, stay here and warm up a little more. Warm up a little. Oh my, what good was a man doing out in the cold? I need to see how I can get back."

At that, Paengdaesan's eyebrows twitched.

But, because her smiling face was dazzling and her eyes were filled with concern, she was truly beautiful.

I didn't even bother saying anything to those who were worried about me, so I just wiggled my eyebrows and said nothing.

Amukhaprap fought well.

Just swing your palm hard and a bloody handprint will fly out and strike the thief.

It doesn't seem like a very quick development for Qing.

In fact, wasn't it the case that even when he fled from Mount Lao, he couldn't reach Qing?

However, the bloody handprint that keeps blinking creates an optical illusion as if it was leaping through the air like a ghost.

Besides, that's actually quite inductive!

So, the clumsy ones don't know what to do and struggle to raise their weapons, and when they get hit on the chest, stomach, shoulders, legs, arms, etc., they get dented and fall down spewing blood.

Only those who were a bit stronger can be struck down with weapons and the leader can be split.

That was the moment.

Amukhaprap's two arms were beating the air recklessly, leaving countless handprints that overlapped and overlapped again, forming a glass window that was completely dyed red.

"Damn it! It's a bloodsucker! Stop it! We can't let it finish! We'll all die!"

The leader (presumably) of the bandits rushes towards him, shouting and spewing out a powerful energy.

It was at that very moment that the remaining thieves all flew away.

"Down!"

With the roar of the Amukhapalap, hundreds of bloody spears were fired at once.

Oh. What was that? Can something like that be done?

While Qing was admiring, hundreds of bloodsuckers attack the rushing bandits.

Pababak, with a loud sound like several people wielding clubs and beating the bandits, the bandits were torn to pieces.

Among them, the leader (presumably the thief) swings his eight-foot long staff in a chaotic manner, leaving behind a trace of energy in a tight trajectory like a net.

He's using his strength, but judging by the way he can't keep up with the Strange Monk, he seems to be a young boy who has just reached his peak.

Bloody handprints caught in the net bounced off the ground with a loud noise like paper breaking.

Hearing that loud noise, you can guess the strength contained in the handprint, even though it was not very fast.

Well, if there's a fight, don't just fight back clumsily, but use your Nengpa Mibo to catch up.

Because the fish cake man was still ambiguous.

That's why the magic explorers were watching Qing's life and death. The more you observe and learn about your opponent's martial arts, the easier it was to deal with them.

The chief thief, who had repelled all the handprints, was panting, unable to control his heavy breathing that was clearly visible even through his thick fur coat, and could only stand with his club as a cane.

However, Amukhaprap only glared fiercely with his cold eyes, and it seemed like he had no intention of finishing off his already exhausted and trembling enemy.

In the heavy silence, only the heavy breathing of the bandit leader and the faint groans of the bandits who were still alive filled the room.

"[It was clearly the study of the Diamond Sutra. You lawless thief, you wicked beast. How could you possibly write such a great teaching when you were nothing more than a thief?]"

But the bandit leader roughly pulls down the fur hat he's wearing, revealing short hair that looks like it's been growing for about a month on his shaved head.

Amukhaprap's eyes widen as if they were about to burst.

Of course, the watching Qing was bewildered.

What was that? Who was that?

"[You're the one who's holding onto your lifeline. I thought you'd go and find that horrible magician, and figure it out on your own. Even the Great Sun Buddha was indifferent.]"

"[You, wisdom that protrudes from your heart, dare a beast of prey to speak of the Great Sun Tathagata? How can you atone for this sin, having spilled the blood of an innocent person?]"

It was Amukhaprap who spoke very monk-like words, but, um, he was chasing me around to steal the absorption magic, so it was a bit absurd.

Then the leader of the bandits shouts.

"[Who was this wisdom that protrudes from your heart! There was a limit to making people miserable! How could you possibly bring shame to people with such a miserable Dharma name!]"

"[What a miserable Dharma name. Just as your nipples stand out even when you wear thick clothes, it was the wish of your parents that your wisdom would be like that among all people in the world.]"

"Shut up! were you going to play with words? You never liked me from the start. No matter what, you're still babbling in my name!"

"[Foolish. Your body will eventually die and return to the Buddha, and it's also a gift from your earthly parents. So how can you be ashamed of your own body and consider it shameful? I wished you would hear it with your own ears, become accustomed to it, and accept it, so I gave you the Dharma name. But can you attain great wisdom and liberation with that level of mental practice?]"

Amukhaprap delivers a solemn sermon, but no matter how much I listen to it, I can't help but think that Amukhaprap was wrong.

No matter how good the meaning and intention are, shouldn't a monk's Dharma name be given to someone with wisdom that stands out in their chest?

"[I have given you the precepts. But since you have renounced being human, you have turned away and become a child. I must take you back.]"

"[Oh, do so. I will wait for you at the fiery entrance to my hell. You will follow me anyway.]"

And then, with a thud, he falls to the ground, his chest protruding with wisdom.

Then, Vairocana, Vairocana, the celestial monk, chanting the esoteric Buddhist mantra, slowly took one step, then another.

That was when.

"Wait! Yumomahop! Stop for a second! Don't kill him. Okay?"

Qing shouts loudly to stop Amukhaprap.
