\chapter{Let's Kill the Bandits (8)}

A thief man, with a long lower body, so-called horse-sang.

The eyes were round, the nostrils were large, and the hair was thick.

Name: Wang Su-hang. Age: thirty-four.

Affiliation. Haeryeongpa Changryongdae.

Review of the second level of the land-

Bam! The world's most beautiful hand hits the thief's head hard.

The thief rubbed his head with his remaining arm, unable to hide his resentful expression.

The expression on his face was like, "Why were you hitting me when I'm answering well?"

Qing snorted at him.

"Hey, were you kidding me? Since when did second-rate brats start judging each other? Even in a one-on-one fight, you two were so close that you want to argue about who's better?"

"Even so, I can easily defeat those second-rate beginners-"

Wow! This was really annoying.

"You guys should think about getting on each other's toes. You're calling me a rascal. Stop it. Haeryeong faction?"

Help! Qing turns her head and looks at Jian Buxi, no, Xue-iri, no, Amukhaprap, no, Paengdaesan.

"Even so, isn't it even stranger that you know about all these idiots? If you're a rambunctious bastard, you wouldn't know."

"It might not be a sect. If it's a sect, it could be a Taoist martial arts sect."

"If you help with theft, was that a different kind of crime?"

"Oh, really? He's quite the mountain. I wonder if I should include him on the list of intellectuals. But he's not exactly smart or clever. He doesn't seem like a strategist, does he?"

"There was nothing you can't say to someone's face."

"If you want, I can put you on the list. But you'll be at the bottom. It'll be Xue Ga-nom, Hyang-i, Lan-ah, Zhuge-i, and Sima So-jeo. What do you think?"

"The list was a bit long. It's a request from my side."

"Oh. So you'd rather have a snake's head than a dragon's tail? You want to be remembered as the most intelligent among the ignorant, right?"

"Do you usually categorize things like that?"

"Yeah. The intelligent and the ignorant. The high-level and the low-level. San was currently the most intelligent of the ignorant, and the most useful of the low-level."

Qing chuckles as she looks at the crumpled expression on Paengdaesan's face.

"Miss Ximen. It's me."

"Ah. Here. Hmm. I'd better not listen."

"Then me?"

"Yi-mei was family. And she's mine."

"Hehehe. Good."

"Me too, me too. I want to do it too."

"Go here and there. First, take a picture of the scenery. Then think about it."

Anyway, let's continue with the interrogation.

A thief man, tall and with a big head.

The side of the head was flat and the nose was huge.

Name: Qingsam. Age: Thirty-seven.

Affiliation, Haeryeongpa Changryongdaeju.

Realm. First-class entrance.

Testimony.

The Haeryeong faction was a small gang that runs a small entertainment district in Seonyeong. They say there was a big case, so they lead their younger brothers and join a group of bandits.

The looted goods were divided and the kidnapped people were taken away by the chief's men.

Next. Next. Next.

Then next.

A thief man, skinny and with short hair.

Overall, a sunken impression.

Name, huh. Age, huh. Affiliation, huh. Realm, huh.

No, were you some kind of space Strange Monk?

Why do you spit whenever I ask you something?

Amukharap's expression distorts as he was attacked with a sharp saliva that tells him to kill without asking questions.

The chief of police came forward with a bang, saying that the chief of police should be questioned, but he just kept getting spit on.

"[Poor child, you have already committed the sin of murder. Shouldn't you repent now and seek the light of Vairocana Buddha? Why do you wish to commit more sins? Without even opening your mouth?]"

Kaaaak, thud!

It was a good attempt, but it was replaced by that phlegm-spitting bloodsucker.

Qing was speechless.

"No, do you think I'll listen to you like that? I'll have to beat you up, support you, crush you, and break you. Then you'll realize, 'Oh, now's not the time for me to be so stubborn about being loyal.'"

"This filthy author, yet the most stalwart of bloodlines on earth, was the Chief. The Chief was a fearsome figure, undeterred by pain, impenetrable."

"Really? Can you guarantee it?"

Qing's eyes narrow.

At the cruel color slowly spreading through the center of his pupils, Amukhaprap coughed.

"You, noble soul, must quickly become a believer and calm your desire to live. Your eyes were like the greatest murderer in the world. Learn from the Buddha, the master of compassion."

"Hey, don't beat around the bush. It's disadvantageous. Those Zhongyuan guys were just a bunch of idiots who came here for money without even knowing anything. The Seojangs seem to know something now."

"I, the Great One, am also frustrated! Very frustrated! Extremely frustrated! My heart was bursting!"

"You're not going to let me off the hook just because I'm the chief, were you?"

"Hmph. This thief has already lost his qualifications as a general. However, a general was a spiritual being; physical suffering does not guarantee testimony."

"What should I do? Should I at least try?"

Qing was smiling brightly.

If this was the case, then isn't there really nothing we can do?

Since I had friends, I chose a relatively moderate method, not a threat, but rather a threat, like leaving her alone and eating dinner.

If you act so uncooperatively, I have no choice but to see blood, right?

Oh, really, really, there's nothing I can do.

"You noble soul, don't speak with a smile. Torture also harms you. Doing bad things for yourself and thus harming yourself."

"Then what should I do?"

"The blade, fire, steel, fists, and feet—all these methods stem from hatred. But to give hatred, to harbor self-hatred, was to accumulate and become mentally ill. But to give was also to give to oneself. This merit was known to heaven, to earth, to Buddha, and, above all, to the other person. This was true influence, and I will show you how to transform through great self-giving."

It was a very heavy-handed sound.

So, Amukhaprap searched the thieves' mountain village here and there, and suddenly started boiling soup in a large pot.

He said he would show me how to teach through charity, but it seems he was trying to win my heart with a bowl of warm soup on a bitterly cold night.

Suddenly, a large bowl of warm noodles came to mind during his military training march in the now hazy past.

Well, certainly, when you're tired, exhausted, cold, and exhausted, a big warm bowl can melt your heart and alleviate your resentment.

Would those stubborn bastards suddenly open their mouths just because they were given a bowl of soup? Isn't that ridiculous?

Or was there something in common between the two?

As Qing watched the behavior with half curiosity and half question, he heard a loud gulp from next to him.

"Hey, were you still hungry?"

"Soup was not rice."

"Huh? Why were you suddenly so cowardly about revealing the truth?"

It was the truth of the matter that Qingdo had no choice but to accept.

Isn't it unfair that something bitter or sweet was a drink, but something salty and oily was a meal?

So, while Qing was watching and Xue-i was watching intently, A-mook-hap-rap, who has scooped up a large bowl of soup in a wooden bowl, approaches the chief who refuses to testify by spewing saliva.

And then, the bulging veins on the back of the Strange Monk's skinny hand that was holding his chin and head meant that the master of Hwagyeong was applying strength.

And then pour in the steaming soup little by little.

"Kwak, gurg, ugh, ugh! Grrr, kulk, puhap, ugh, keuk!"

As the boiling soup goes into my nose, I immediately let out a scream, and as I scream, soup also fills my mouth.

The chief thief, with his arms and legs tied to a child's chest, flailed his body like a fish out of water, twisting and bouncing around in a desperate attempt to escape.

The head that the master of the firefighting master has decided to hold was fixed in place, so he cannot stop the desperate sounds of "gulp, gulp, gulp, gulp", "slur …

Qing looks at the sight and slams his fist into his palm.

Ah. Giving was exactly like that.

"Keukgeuk, keuhak, [Okay!], gulp, creak, [Stop], owak, slurp! Phew, [I'll say it]. Keuk, [Please!]"

Qing was impressed by him.

Just by giving, you can really open your mouth and let the truth pour out, right?

An amazing sight of enlightenment being achieved through sacrifice without the use of blades, fire, steel, fists or feet.

"It has no taste. It's spicy, bitter, and salty."

"Hey, come here? Have you tasted that bird again? If it doesn't taste good, why were you insisting on serving it to me?"

"Yes. Yes. It really was tasteless. Try it."

Qing takes the bowl and slurps, "Hmm, I think it'll be okay if I put some sugar in here."

It's originally spicy, bitter, and salty, but if you add sweetness to it, isn't it the most delicious soup?

Anyway, back again.

Name: Changhwamima. Age: thirty-one.

Affiliation, Soreumsa-

"[what!?]"

Amukhapalp screamed out loud.

Then, Peng Daesan turns his gaze to Qing.

As Qing was listening, tapping her ear, she signaled to listen more.

"Why, why would a monk from Soreumsa commit such a heinous theft!"

"[Hmph, croak, kaak, damn it, sometimes you have to carry the torch and jump into the fire for the sake of a greater good. If I don't go to hell, who will?]"

"[What kind of cause was that?]"

"[Tobun.]"

At that, Amukhaprap flinched and staggered like a person stabbed by a blind arrow.

"We will reclaim our great empire. It was not too late for you. It was time to break free from the puppetry of that oppressor, the enemy of Zhongyuan, and join the true destiny of the Western Generals."

There was no answer to that.

Qing slowly grasps the hilt of her knife and makes eye contact with her friends.

It meant that something was not normal, so prepare to leave.

The group quietly straightens their postures, but why was Lee filling the water bottle with soup?

If you freeze soup and make a sword, what should you call it? A soup sword?

At that moment, when the sound of water rising was so loud and tension was falling in the room, the angry voice of Amukhaprap suddenly shouted!

"[This, this, the ghost of Tibet has possessed you! Yes! Tibet was great! A great empire! The Tibetan empire that once ruled the world! And all you do for it was this kind of petty theft!]"

"[I know you. Yamuk-Hiparang. They say you're the greatest of the traitors who call themselves Zhongyuan' lackeys in the Blood Thunder Demonic Cult. Indeed, how much blood has been shed by the Seojang's martial arts? But there's still a chance. It's time for you to atone for the sins you committed against the Seojang and use them for the Seojang.]"

The term "Han-gan" was a derogatory term meaning traitor, national traitor, or turncoat, and was also the most offensive of the insults used by the people of Zhongyuan.

Hangan was a curse word used against the Han Chinese, but it seems that's how it's translated to the Qing.

"[Mingma, you foolish Mingma. were you willing to shed the blood of the living for an empire that has already fallen?]"

"[You damned bastard. was our chief's long-cherished wish nothing more than a ruined past to you? Look, look at this land. Look at this land that Zhongyuan bastards have arbitrarily taken away. Look at our chief's children. Look at the children of our people who speak the Zhongyuan language, have Zhongyuan customs, eat Zhongyuan food, and think like Zhongyuan people, and were gradually disappearing.]"

"[Do you deny our children because of that? They were still the children of our leader. And at least you have no right to say such things. Tibet, how did that empire that ruled the world fall? It was because of the wickedness of you Podalap bastards that the world was in mourning.]"

"[As expected of a nerd, we can't communicate.]"

"[Is this truly the intention of the Dalleorama? To start a war with Zhongyuan for that meager power? was that why you seek to sow discord and hatred between the people of the West and the Zhongyuan?]"

"Haha! Sowing discord? Sowing discord? Then you're telling me to be friendly with those enemies who stole the chief's land? was that something a descendant of the chief's bloodline would say? You scoundrel! You filthy traitor!"

"You were just full of hate."

Amukhaprap puts his two hands together and recites the Buddhist scriptures.

Then at some point, bang!!

With the sound of a large hammer breaking, the body of the thief, the upper part of his lower body missing, falls over and starts convulsing.

Amukhaprap, who had been killing the body, simply looked down at the body coldly.
