\chapter{Let's Kill the Bandits (5)}

Nanga Moonlight Sword. It was a pseudo-iron-thrust sword with a half-foot spiked iron club and two and a half-foot iron bars attached to it, connected to the handle of the Moonlight Sword.

The reason why it was separated was because it was against the law.

Originally, national law prohibited more than four ships of warships.

Of course, there were officials who neglect their duties and just play around, using the good excuse of being inviolable.

Since they were officials who do not work for no reason, they do not actually catch them and beat them with sticks for breaking the law.

The long sword used by Choryeo was almost five feet long including the handle, but to the eyes of the officials, it appeared to be about four feet long.

Thanks to this, the martial artists take the laws of the land very lightly.

For ordinary people who were not part of Wulin, the law of the land was truly fearful and scary.

To the officials, martial artists were people who, if they were unlucky enough to poke them, will see bloodshed, and if they were lucky enough to be safe, they will see bloodshed. However, if you poke commoners, they will start to lose money, so everyone will beat them up.

Hey, you hit it too, the money's coming out fast!

So, the old man, who was afraid of the law, made weapons by barely keeping up with the law.

The Nanga Moonlight Sword was the result of a trick.

The long iron bar of the Nanga Moonlight Sword, with its large sword attached to it, entered the thief's shoulder and swung vertically.

The blade barely stops after passing through the side and reaching the pelvis.

The severed body collapsed, and the arm attached to it dangled limply on the frozen floor. A clean cross-section of the shoulder blade and ribs was revealed for a moment. But even that was fleeting, and soon it was obscured by the gushing blood.

Still, it wasn't completely cut, so how about stitching it up properly? Of course, I don't know if the best doctor in the world could come and stitch it up right away. But anyway, well done.

Qing releases his grip.

As the heavier weight of the Nanga Peak naturally heads towards the ground, the hand that reached the handle of the Moonlight Sword smoothly turns to the opposite direction, and the weight cuts through the air in the shape of holding the Nanga Peak.

Kyungcheondaeseongmagon. First, Yu Seong-twi.

I thought Qing was a pretty interesting name.

Didn't the original Yu Seong-twi refer to a weapon with iron weights attached to both ends of an iron chain? Of course, it's not Yu-ryu (flowing), but Yu-roo (playing), and the two star-shaped iron weights attached and twisted together to form a shape that resembles playing, so it's called Yu Seong-twi.

Wasn't the poet quite a humorous guy?

Suddenly, the awe of a man who watched the falling star flashes through my mind.

It's not just a meteor in the night sky.

A fallen star that unfortunately fell nearby.

A spectacular explosion that causes a splendid mansion to be torn apart into pieces, violently disintegrating in all directions.

However, the pieces radiating in all directions contained pieces of flesh and bone from his wife and children.

But instead of crying out in sorrow, the warrior sat down, crossed his legs, and transformed the destruction he had witnessed into martial arts.

It was a pity to lose a wife and children, but as was the case with Liu Bang and Liu Bei in the past and countless other heroes and valiant men after them, a great man can abandon his wife and children and take in new ones at any time.

If you feel sorry for such trivial things, how can you accomplish great things?

A star has fallen before my eyes and I have come to enlightenment, but were my family important?

Of course, it was the idea of ​​a human being who deserves to be punished by heaven and earth.

Of course, the man was pointed at, expelled from the sect, and had to run away in an ugly manner before breaking his dantian.

Thanks to this, a new martial art appeared in the world.

It was a painting depicting the great fall of a giant star that made even the heavens tremble in fear.

The only regret was that the weapon the man learned was a thorn.

Why Gonbeop?

If it was a sword or a dagger, it would have been gold instead of red, and if it was good, purple too.

No, should I be thankful I'm not a martial artist? If I had been a martial artist or a martial artist, I would have just lost my wife and children to create a blue, or at most, a martial art, and become a wreck.

Suddenly, Qing's mind flashed as he saw the person on the horizontal bar burst into his grasp.

Oh, seriously, hiya. This was awesome.

The lump of iron, Nanga Peak, clanked again, from one thief's insides to another, yellow lumps of fat and flesh clung together until it looked like a giant lump of flesh.

Well, I should try that.

Qing grabs the blade that was being used against me with her hand and pulls it away.

That's what the bandit leader did, that human meteor, that's what I learned to do.

A monstrous force that easily dragged a man away. The bandit, unexpectedly losing his balance, came running, and Qing's left foot slammed into his ankle, sweeping the floor.

But haa, hold on.

It's not going to work with my current physical condition. If my still-fragile bones start to crack, I'll have to wait another twenty days for treatment.

Qing leg flashed, and in an instant, both feet, erected as straight as bamboo, fell down with incredible speed, crushing the thief's knees and leaving footprints on the freezing ground.

There was a knee, there wasn't.

The thief expresses his feelings with a terrible scream.

A sweet performance that was sweeter than any other instrument, it makes you feel excited and somehow makes you feel warm all over your body.

Oh, right, Yoo Seong-twi.

Come to think of it, I think the kicking technique, or more precisely, the kicking technique where you hit with your heel, was also called a yuseongtoe.

This martial arts creator knows how to play with words.

Now that I think about it, let me say this.

Qing fur coat fluttered loudly, and then Qing heel shot up and—whoa! The thief's collarbone was shattered and dented with a single blow.

Qing'er whirled, lifted her arm, and stood elegantly, spinning backwards - slipping.

"Huh?"

"Eww!"

The things lying on the floor were thieves, their limbs and bodies were completely torn apart, and their remaining lives were fading away, so it might be a little unfair to accuse them of being careless just because they stepped on them.

Qing'er's buttocks were pounded not with a sound but with a form like that.

The tailbone was the first to hit the frozen ground!

It's not like the tailbone can't support the weight of Qing plus a heavy weapon, but that doesn't mean it can't suffer.

The tailbone, which punishes its careless owner with a pain that makes it scream out involuntarily, says, "You're paying the price for ignoring the organ that has degenerated!"

"Dead!"

At that moment, a bandit targets the fallen Qing.

It was a great surprise attack, but Qing was originally someone who didn't care about appearances at all, and since her first job as a beggar was to enter Wulin, she was a person who could use such ugly methods without any hesitation and mercilessly.

Qing rolled backwards ugly and stretched out its limbs, making it look like it was standing on all fours like a wild beast and raising its head.

The gaze that shoots at him was as ferocious as a beast with the color of a thousand years, so much so that he could be called a beast itself.

And as if Qing's knees were about to touch the ground.

The knees of Qing were organs for propulsion only.

Then, with a fierce attack like a tiger, or rather a female tiger, a long grip grabbed the bandit's face under his fur hood.

An ice dragon rises from Qing's shoulder, wraps around his arm, and rides down, touching his palm with a thud!

Somewhere in the deep waters, infinitely deep, deeper than you can imagine, down there, in the pitch-black depths of the ocean where even the sun's light cannot reach and the warmth fades, it's just a dark world, a terrifyingly transparent illusion of ice.

All sides were not the same shape, each one a different shape, forming a sphere of boundless, ominous ice, and suddenly, with a heartbeat and a wave, its solid frozen state trembles with a strange ripple-

Hmm? was this ice cream? Okay. I'm busy right now.

Leaving behind the iceberg that was writhing in a hurry with an urgent look, Qing's image suddenly floated to the surface.

It seems like we've knocked down quite a few, but there were still a lot of bandits left.

Hehehe, there's a lot left?

Qing drags the bandit's face with his left hand and swings his Bbung Bbung Nang-A Moonlight Sword.

Raising it high once in a while was the most effective way to use the thief shield, the thief profession.

Then the thieves hesitate and distance themselves.

Loyalty to thieves? You leeches, sucking the blood of innocent people, do you maintain loyalty to one another?

Have you ever seen such disgusting kids in this world?

The thief cannot attack rashly, so he slowly and cautiously leads the standoff.

Qingdo takes a deep breath and turns his head tensely, wondering where and along what trajectory to draw the line so that it can play a pretty and pleasant scream.

After continuing the standoff like that, it broke out!

The sound of ice breaking. The handle of the thief's shield, the facepiece, was frozen so much that it cracked, forcing itself out of his grasp.

The flesh and muscles of his face were torn and neatly cut off, leaving a white skull rolling on the floor.

Not only was his face a face, but his eyes had turned to ice beads, and he was even more shocked by the sight he had lost, as he held his eyes shut.

What was it? I think it's around thirty.

Do I have to count to thirty just to freeze and shatter someone's face? was this ice-cold technique even practical?

With such insignificant martial arts skills, you tormented Gunyeong, the descendant of the Ice Palace, and eventually drove him out?

What the heck, were all the Ice Palace guys idiots?

Gunyeong, although he's a bit useless other than his looks, if we had used the highest level of intelligence in the province, Xue Ga-nom, well, we could have taken over half of Zhongyuan right away.

It's still a blue that has a lot of room to spare.

And the leisure of the strong was the despair of the weak.

The thieves, who had been preparing their weapons while keeping an eye on the situation, took a step back, then another step back, and then hesitantly retreated. At some point, someone shouted, "Wow!"

"Not a human! \#\#! \#\#\#!"

With the awkward Zhongyuan language, the words of the chief, the Nachalnyeo? What was the Nachalnyeo? Are you insulting me now?

Nachalyeo was a Strange Monk and the mother of Seojangin in the legend of the birth of the Seojangin people. She mates with a monkey and gives birth to six children, who become Seojangin's ancestors.

However, at that time, the evil spirit Nacha had not yet converted to Buddhism, so it was the greatest of the demons that devoured ten thousand people.

The Nachalnyeo was the female Strange Monk that the Seojang people fear the most.

Of course, Qing doesn't know.

It would be more amazing to know.

I'm not even a chief, so I'm not really curious about the birth of another nation.

I had no interest in the story of the birth of the Han people or Zhongyuan people, but I learned about the Qing through studying Taoism.

Anyway.

It was true that the hands of the Qing were not human, so they were already causing fear.

At such times, the first one to jump out occurs, and the fighting spirit was instantly broken and broken, and everyone turns their backs and runs away as if they have only just realized that the choice was to run away.

The bottom was not safe either.

As the thieves, crippled and flying through the sky, screamed one after another, the terrified fugitives ran up the hill, up and up again.

Because the brick wall that the captured men had built with their blood, sweat, and tears had never been as strong as it was now.

"What! Stop! I want you to fight!"

I don't know if he's a captain, a commander, or a private, but since I don't know, I'll have to grab him and ask.

"You idiots! If you run away, you'll soon meet that Strange Monk… Ugh! Get out of here!"

The man who was pacifying the fleeing bandits sees Qing attacking him, throws down the iron bar he was holding, and turns away in fear.

However, the momentum of the iron bar flying towards him while spinning was so fierce that Qing stops and raises his hand to grab the iron bar passing by.

Chiik, the iron bar that does not stop rotating even in Qing's grasp, filled with all the energy.

What was that, a burning palm, a steel wire attached to your hand, a spinning tornado, a club thrown, a dagger?

Meanwhile, the leader of the bandits, who was the last to retreat and escape, quickly overtook them and dug in through the door of the bandit camp.

No, what makes that kid so fast?

But what was it? Will you always be first and last?

I wonder if the term "true commander" originally meant a high level of light combat skills where one runs away last and stands at the forefront.

Moreover, the first thing he does was to go in and the door starts to close with a squeak. He intends to abandon all the thieves, whether they were his subordinates or colleagues, and close the door first.

Qing watched the scene in disbelief.

No, what can I do if I run away there?

It was a wall built only one chapter high.

Of course, to Gunyeong, it's 'a whopping' one sheet high, and to San and Yi-mei, it's one sheet high, so they'll feel it based on their friends' insignificant level.

But this body only has one.

What good was that paltry barrier in front of a true master?