\chapter{Let's Kill the Bandits (4)}

A group of bandits rush down at the command of the leader or something to attack.

Because it was a dark night, the black auras blooming with colors create countless lines in the air.

To Qing, it looks like they're coming down in a group carrying glow sticks that were about to go out.

The black light had to shine just enough to be like that, the level of light that was on the glow-in-the-dark dinosaur in my nephew's room before he left.

However, no one can see that this was an ordinary group of thieves.

Which band of thieves in the world would each have a subtle glow on their weapons and spread weeds?

Even among the regular mountaineers of the Green Forest, more than half were just young men who use their strength for external attacks.

This force should be called a regular combat unit, not a bandit force.

Is it even possible to mobilize a sect that has taken over a city?

I would say it was truly a powerful force.

But, strength was always relative.

Qing pulls the left arm over his shoulder.

A fierce and murderous feeling that rises up in an instant.

A woman's life flashes through my mind.

The endless abuse of my childhood, the fact that my father was the one who sold my young body before it could even fully mature. The miserable lives of women in similar situations, comforting each other and slowly falling apart, just barely able to survive, and fire, knives, blood, screams. My sisters, the only reason I held on to life, when even that thin, fragile, and fragile cord I had barely been able to breathe was cut. Hands clutching my resentment so tightly that they broke, hands shaking with a clenched fist, blood drained and turned pure white, hands so beautiful they were almost transparent.

Behind the back of Qing's hand, the demonic hand formed by the woman's resentment adds strength.

With its long, twisted claws jutting out like those of a beast on its emaciated frame, its shape alone must be something terrifying beyond compare.

But the hand that flashes with pure white light, that terrible form, was just a transparent evil that wraps itself in some sublime beauty.

Small hands.

White was the ugliest color.

Because it was a terrible color that muffles the terrible screams of the soul, like snow that simply covers the suffering land.

Qing nails lightly grazed the bandit's stomach, and only the hem of his clothes was caught between his fingertips, which he roughly tore off.

However, a white demonic hand covered with a layer of cloth behind the back of his hand digs into the man's stomach.

A grudge that tears, not cuts.

Wow, hot blood rushes to my face.

The hot temperature that was originally boiling with life, but now cools down to a coldness that was full of blue.

Huh, I can't help but let out a sticky laugh.

Yes, all those dirty boys should be slaughtered. Everything, everything.

Perhaps even Master would praise it, um, Master, no, Master said to beat him, not kill him.

Hmm. Killing them all was a bit much, isn't it?

What if we kill half of humanity?

In the first place, were all men possessed by a demon of lechery? No, it's normal for men to be possessed by a demon of lechery because they were horny at twelve o'clock every day, right? If not, then it's abnormal.

That being said, there weren't many people who were blinded by that sexual desire, so isn't that where the line between humans and beasts lies?

And then, why am I even worrying about this? Does it make sense to kill someone just because he's a man?

Ah! This was thought, this was magic.

The violent image of the minority demon and his true intention to slaughter every man in the world made Qing shudder.

It was the moment when I finally truly understood why magic was called magic.

Now, finally! At last, at last!

It's a good thing I'm in the mirror.

If I had been in a state of shock, I would have been completely out of my mind and almost given birth to a male serial killer or male genocidal exterminator in Zhongyuan.

But somehow, looking at the bandits makes me really hate them. This was really a bit dangerous.

Is the magic dangerous, or was it because it's purple among the ten greatest magicians in the world?

Then I guess I'll have to try other magic too.

An amazing event! A scientific accident!

Wouldn't it be possible for Qing to transcend his background, his liberal arts, and achieve the evolution of humanity itself?

What if you greeted someone and they slapped you hard in the face?

People with liberal arts backgrounds will immediately cut ties with this crazy guy and avoid him.

However, the scientific thinking of those with a science background was not like that, so they seek to find out the exact cause by investigating the causality of the event.

Did you get slapped because you said hello? Or because you pretended to know me?

Or maybe he was just in a really bad mood right now and wanted to slap himself.

Yeah, maybe I mistook you for someone?

To find out, we can change the variables and try speaking in different ways.

So, Qingdo tried talking to the magician in a different way.

Qing's left hand draws a different hand shape.

Those long, slender fingers spread out, and soon four diagonal lines were drawn with four strong energy lines.

A vivid, blood-red skeleton appears in the center of the sunset, and there was also a strange optical illusion that makes it seem like something heavy was slowly sinking down.

Taesan blood ancestor, the first blood ancestor manipulation cancer meridian.

As the sword flickered, a second-rate thief hurriedly raised his sword to block it.

It's an absurd situation where a second-rate subject dares to confront the martial artists Hwagyeong, so how could it be stopped?

Four deep furrows were dug for the thief.

The fallen thief, in Qing's left hand, had a long sword dangling from his fingers.

Qing's arm snapped, and the sword, which had been bitten off, fell down unsightly and clattered.

Qing's eyes tremble.

Wow, as expected, the cooking method was really good.

As the name suggests, Taesanhyeoljo contains a mysterious and heavy element in the method of making. Since it was a mysterious element that does not fit the method of making, it seems that it was overcome by adding a deep murderous intent.

Well, it doesn't seem like there's anything particularly swaying you?

Isn't it natural for killing intent to rise during battle?

Front wheel drive, ugh, I'll change it all.

This rough, shattering sensation, was this what it feels like to cut someone down with a chainsaw?

This was crazy, I'm going to get addicted.

Heuksalmajang, kekeke, I'll destroy them all.

As expected, this crushing sensation that hits you hard was different from cutting, slicing, and tearing, and it has a refreshing feeling of being completely pierced. Wow, good, good.

Baekpalsura Sword. I am a dangerous beast right now!

Well, but it's a bit dangerous when the canines and jaw were itchy because you want to bite them with your mouth.

But even so, biting it, um, really, really pulls. When you bite into raw flesh with your teeth, the aroma fills your mouth, how sweet it would be, gulp, ah, my mouth was really watering.

Should we try? Maybe we can bite a little during the life-or-death struggle? So right now, um, no, why were you like this, Jijiya, it's cannibalism.

This guy was dangerous again.

After looking at the magic, here's the conclusion.

Even within the magic arts, there were types that were dangerous and extreme in their own way, and types that were not.

Of course, the term "magic" itself includes not only the types that infect people with demonic powers, but also those whose training methods were evil or particularly cruel.

Even though I don't know much about magic, I think this was a huge realization and growth for Qing.

However, if someone knew about this, wouldn't they be very shocked and outraged?

The woman who slices, tears, and destroys people was actually enjoying and demonstrating the thoughts of the devil, so she was very relaxed and just lying around.

This was an obvious fact.

Qing was very relaxed.

When you swing the vicious giant weapon, the Nanga Moonlight Sword, your enemies will be cut down one by one.

Although the close range has become more vulnerable as the length has increased, the magic attacks that alternately spread across the left hand break, tear, and rip apart, causing endless slaughter.

Before anyone knew it, Qing had dug into the middle of the bandits' den and made his presence known through the gushing blood.

"Xiao-mei!"

With a worried expression on her face, Jian Buxi takes a step forward, trying to advance towards the isolated Qing in the enemy lines.

But soon she took a step back again, because Peng Daesan's hand had caught Jian Buxi.

"Leave her alone. She has the guandao, but if things get dangerous, she'll just come back."

"But, it's dangerous."

"It must be much better than before. I can clearly see her lingering around, pretending to be some kind of mother, protecting her children, and then turning a blind eye to them. Isn't that right?"

"Huh? Hmm."

"At least she won't have to worry about you getting hurt. If you do, that foolish girl will cower and run by herself. So don't waste your time and protect yourself."

"Ung…"

If Qing had listened to him, she would have been arrogant and said, 'What's the point of protecting someone when you can't even beat Yi-mei?' and would have been sulking, saying, 'There's no way a low-ranking person can worry a high-ranking person'.

Qing was so excited to see blood after a long time that she missed the chance to tease him.

A long way behind, Xue-i-ri, who had thrown the Amuk-hap-rap into a crack in the sunken rock mountain, immediately lifted her body and climbed the hill.

On the way up, you can see bandits who have lost both legs and were crawling on the ground, groaning in a gloomy manner as they die.

Xue-i-ri stared blankly at the sight without any expression.

"S-save me……"

Xue-i-ri approaches and gently reaches out her hand to the severed thigh.

The Ice God's Bing Baek Shin Gong, with its immense cold energy flowing out, reveals the Ice God's true power without restraint on this already cold winter night.

The affected area freezes solid in an instant.

The thief's expression, which had been trembling with anxiety despite his earnest gaze, now looked much more relaxed and relieved.

"Go, thank you……."

The corners of Xue-i-ri's mouth slightly curve at that.

It was filled with a cold, sarcastic sneer that didn't change the shape of the eyes at all.

\textit{Young Lady Ximen always said that wicked people should not die in peace.}

\textit{So, I just extended his lifeline so he wouldn't die easily, but how would he survive anyway?}

Freezing like that, and freezing again, freezing the arm of the thief whose arm was torn off to do something like emergency hemostasis, freezing the stomach of the thief whose stomach was burst, freezing the forearm of the thief whose arm was torn off, and freezing the area around the missing shoulder of the thief whose arm was torn off.

For some reason, guys keep appearing with their arms and forearms ripped off in a horribly bad way, their bones and long, stretched muscles hanging out.

As I climbed up like that, I saw two people blocking the narrowing valley above.

Anyway, one of them was not interested.

What catches Xue-i-ri's attention was the remaining one, Jian Buxi's incredible inaction.

With a strange, yet somehow slimy and soft gesture, I deflect the blade pointed at me and naturally grab the thief's wrist as he slices through the air.

Then, as if a pair of well-matched swordsmen had been put together, the thief's body naturally rotated and spun around, then soared high into the air.

The remaining Jian Buxi on the ground had one forearm left, so he swung it like a club and slammed it into the thief's head. The thief fell down violently, his lower body facing upwards.

Both Lady Ximen and Sister Kyeon were not ordinary women, so I wonder if they formed a sisterhood with strong women.

A series of scenes where the two engage in a power struggle between their tightly clasped hands, then fierce smiles and lewd laughter intersect, and soon they politely raise their glasses on the stage beneath the peach blossom petals fluttering in the breeze.

Then, as the two suddenly turned their heads and waved their hands in greeting, a slender woman with silver hair approached from behind…

Thump!! The heavy sound of a crash from the sky shatters Xue-i-ri's strange and impulsive imagination.

The bandit, whose shoulder blades were roughly torn off, fell and rolled down the slope, stopping with a thud at the sole of Xue-i-ri's outstretched foot.

It was the moment when I understood the identity of the strangely numerous thieves with their torn arms.