\chapter{Let's Kill the Bandits (9)}

For a long time he stood there, his head tilted askew, the shadows of fire cast dark shadows on his sunken eye sockets.

yet.

The Strange Monk takes a step forward.

Bang! Bang! Bang! Without even thinking about using the soup of truth that they had painstakingly prepared, the heads of the black-haired thieves exploded one after another.

Thud, thud, thud. Corpses with their heads smashed open lie by the fire in the cold night.

"Eek!" "Save me! Save me!"

The people of Zhongyuan, unaware of the blood flowing from their half-melted wounds, struggled to get away from the Strange Monk, flailing their limbs.

Of course, Amukhaprap had no interest in Zhongyuan bandits.

The foolish thing of crawling on the frozen ground and making yourself sick and bursting your wounds.

So you shouldn't have sinned.

It's not that I'm scared because my feet were numb because I know I did something that will kill me.

"[This fucking bastard-]"

Bam!

"[See you again soon-]"

Bam!

The Amukhaps who break each and every head were Amukhaps, but the Kakamos who face death with a blue-eyed hatred without even asking for their lives were also quite jingling-

"[Save me, save me. Ambassador, my disciple, my disciple has done wrong.]

It was a terrifying thought, a thief begging for his life.

"You, little puppy. You've been so fearful and trembling since childhood. If you've made up your mind, you should see it through and face death with dignity. Why should you leave your worries to me?"

What, was your Buddhist name Little Puppy?

In Qing's eyes, he was a big man who seemed like he could communicate well with Zhuge, even though he was a small puppy.

"[The disciple was blind and took the wrong path. Please, have mercy, have mercy on him.]"

"I cannot tell whether you truly repent, or whether you simply fear death and continue to sin with lies. Would you, then, close your dantian and return with me, confessing your heinous sins to me? If you will, I will not doubt your sincerity.

"[Yes, I will do that.]"

The Strange Monk raised his eyebrows once.

Haaah, he lets out a deep sigh and recites the sutra, passing the small puppy and heading towards the remaining bandits.

He looked down with a sad and sorrowful look in his eyes, his lips trembling, as if he had something he wanted to say but was hesitating and unable to say it.

"Kill me. I will not beg for my life like a priest."

From what I can see, it seems like they were disciples of the temple of Eomuk, whose faces I know.

But everyone just keeps their mouths shut, spits, or mutters curses and curses in a low voice, so isn't it just an attitude of wanting to die obediently?

And so, for some reason, the sound of a head being broken seems to resonate in a sorrowful way.

Finally, the only one of the black-haired bandits who caught his breath was a small puppy, and a strangely aged monk was trudging towards the group's fire.

Qing pretends not to know and looks inside.

"What was it? were you going to let him see it?"

"That thing's name was Deokgilgiju, a happy bastard in Zhongyuan language. He's a disciple of the great Blood Thunder. Some of the bandits were disciples of Blood Thunder. It's shameful to have my face etched on the great one."

For reference, Gaesaekki was not a given name for Amukhaprap, but a common nickname in the West. Deokgil doesn't simply mean happiness, but the ultimate happiness that leads to nirvana, so it's not a bad name for a monk.

Originally, if you try to explain the meaning of any name and use frivolous words, it tends to sound unpleasant.

Even in the Qing Dynasty, it was a cold year for the West Gate.

"This was a shocking revelation, beyond anyone's belief. That's why testimony was necessary, because no one can believe it. It's a tool we'll use to prove our guilt by taking us to the Great Self's headquarters."

Since several disciples of the sect were involved, they were saying that they will take them back and make them testify.

"I feel sorry for you. I, the great General, apologize on behalf of you, the humble invaders of Zhongyuan, for the terrible crimes of some unscrupulous generals."

Amukhaprap put his hands together and bowed.

"But you're not the ones in charge. You need to report this to the Kunlun Sect immediately. But if the authorities don't know about it, I urge the Wulin Alliance to step forward…"

Amukhaprap explains.

The Zhongyuan were uncivilized.

Because the Buddhists, Wulin, and the government were all separate entities, it was an inefficient mess.

The West was one in which the Buddhists, Wulin, and the government officials were all one.

The ruler of the West Chapter was the monk, and the West Chapter martial arts world was also led by the monk.

How simple it is, and how the Buddha's will was to establish a nation in the Saha world. No other nation in the world can achieve such greatness.

However, the problem was that even in the great sutra there were many departments, that is, many sects.

Even if they worship different Buddhas, they will eventually meet in the same paradise. Why do they hate each other and regard each other as enemies, and this has continued for a thousand years since the fall of the Tibetan Empire?

"Isn't that contradictory? You call yourself a great general? Fighting for a thousand years on two sides was considered greatness?"

"You were a brave man, but the Great One already knows your empty head. Don't emphasize it. And yet you were great. Because…"

In fact, it's better to fight.

During the Tibetan Empire, monks who did not fight each other committed all kinds of evil acts, so the daily life of the general was filled with tears of blood.

Because this was the national law of the Tibetan Empire.

Did you look at the monk in an arrogant way?

Gouge out the eyes of yourself and your five neighbors.

Are you referring to a monk without permission?

He cut off the wrists of himself and his five neighbors.

Did you say something rude to the monk?

Pull out the tongues of yourself and your five neighbors.

It was a truly frightening law.

Because the standards for enforcing the law, whether presumptuous, reckless, or insolent, depend purely on the monk's mood.

In other words, the monk could easily kill a civilian if he was in a bad mood for even a moment.

Even the punishment of Tibet was to tie up six households and have each member of the six families pay the penalty.

"No, where on earth would you find such a filthy law? It's the perfect law to ruin the country."

"You were right, you brave soul. That's why you failed."

But the legacy still remains.

Respect the monks and the common people. The monks were noble and the common people were lowly.

The monks of Seojang still reign as nobles, and have fought for a thousand years with the ambition of unifying Seojang, taking sides under the name of sect.

War was a cruel thing, so the lives of the common people in the West were not easy for a thousand years.

Of course, this was the director's situation.

Rather, the Tibetan people of the former Tibetan Empire's territories, Qinghai, Sichuan, Guangxi, and Gansu, which became Zhongyuan, were living much more peacefully than the common people of their home country.

So, Amukhaprap left the West to live as the West, and wanted the West Jang people and the Jang tribe of Zhongyuan to live well as they were.

The reason why Ahaprapdalhaptaeksa and Hyeolroeumsa moved their base from the land of Seojang to Qinghai was to protect the Jang tribe living in Zhongyuan.

"Um. But?"

"Even the great Englishman himself does not know the details. However…"

It was unknown whether the homeland decided to turn its hatred outward, or whether the new Dalai Lama united the sects and achieved unification.

Dalai Lama, the Dalai Lama in the Qing homeland, was a title used to refer to the king of the West.

It means the teacher of all, and was the highest teacher, that is, the religious leader, and the head of the Seojang was the only one who was in charge of the Seojang martial arts world, so it was a position that also serves as the king of the Seojang and the leader of the Seojang martial arts world.

When I hear the name Dalai Lama, I get the feeling that he was a symbol of peace.

If this was the case, isn't he just a dictator, with added cruelty?

Well, that's just because the title was unfamiliar.

If we just say king, there were tyrants and virtuous kings, and we do not consider the two as one.

Even in the hometown of Qing, weren't there 'that Injo' and King Sejong the Great?

However, unfortunately, in this primitive, ancient, and uncivilized Zhongyuan, all the Dalai Lamas of the past were nothing more than ruthless tyrants and war mongers disguised as Buddhists.

And now the war maniac has turned his gaze to the ground.

Our Blood Thunder Thunder will also do its best to block it before it happens through various means.

But things don't always go as planned, so if something goes wrong, war breaks out.

So, you should inform the Kunlun Sect of this so that they can prepare in advance, and I also hope that the Wulin Alliance will step forward.

Even if something goes wrong, I hope it becomes a fight between the Western martial arts world and Zhongyuan martial arts world.

Official duties were inviolable. Officials will not interfere in the fights of Wulin, but will rather welcome and watch.

If that ignorant central government official steps in, the West will be completely destroyed.

"If that's what Eomuk said, wouldn't it be better to just let it fail? Even now, the chiefs in Jungwon were living better lives."

"foolish!"

Hey, Amukhaprap, give me a shout!

I don't care about the destruction of the prologue.

But war was something that creates hatred between nations, and when a fight like that happens, the sparks fly to all the tribes.

Even if that's not the case, what will become of the common people of Zhongyuan?

How much blood will be shed before the war?

The common people of Zhongyuan were somewhat unconvincing, as their usual words and actions were those of people who only care about their own interests.

But apart from being unconvincing, it's not wrong.

"Wait, wait a minute. Fish cake, come this way."

Qing and Amukhaprap headed to the brick building of the bandit camp.

"[Actually, I know how to speak Xizang. It's a bit embarrassing to say I know how to do it, but I can do it.]"

Originally, the fact that the chief's words were possible was kept secret.

Because he was a very suspicious, inscrutable, strange and eccentric guy.

But now I think I can trust it a little.

Because he was a Strange Monk who had revealed not only the overheard dialogue between the chief but also his own judgment.

"Amazing! How can you, valiant one, speak the most beautiful, yet difficult language on earth!? Even the way your valiant tongue articulates was not like that of a Chinese person, a dumb, clumsy idiot! Absolutely perfect!"

"[Usually, when someone from another country speaks your language, even if their pronunciation was a bit strange, don't you say they speak well?]"

"Nonsense! Words that don't work, the unacceptable howling of a dog! My own words are perfect! But even if I, a member of Zhongyuan, speak for fifty years, my words are still the same as those of a crippled person. This was precisely what proves the greatness of the words of the Western General."

The expression on his face suddenly turned sour.

"[Are you saying you speak perfect Zhongyuan now?]"

"That's right! Just like your beautiful, noble words, my great Jungwon dialect skills were flawless everywhere. Everyone in Jungwon knows I'm Jungwon."

Amukhaprap's words were firm.

Qing was even more absurd.

This was such a heartfelt statement, what the heck.

"Huh. That's right. You, my valiant one, are actually Xizang?"

"[Hmm. I can't say for sure. But why do you keep speaks in Zhongyuan?]"

A strange situation where a person from Zhongyuan speaks the West and the West General speaks the Zhongyuan.

"[Yes. My admirable child, I was momentarily confused and ended up speaking the lowly language of Zhongyuan. Why then do you wish to meet with me alone?]"

"[You can't just let go of 'lowly Zhongyuan' huh?]"

"[They say a Buddhist never speaks falsehood. Look now. Your voice are so beautiful, not in the loud, pig-squeaking language of Zhongyuan, but in our soft, song-like language. This is the first time this monk have realized this. Won't you take refuge in the Buddha? If you recite the sutras in such a voice, all people will involuntarily listen, and the merit will return tenfold, a hundredfold. How delighted the Buddha will be.]"

At Amukhaprap's soft words, Qing roughly rubbed the goosebumps that had appeared on his arm.

\textit{No, sir, I really can't get used to this.}

"I'm a Taoist in my own right, you know? Of course, I'm a bit of a pseudo-Taoist, but whatever."

"[Why are you making pig noises again?]"

"Well, just in case. Um, in my opinion, that Deokgilgiju? He's incredibly suspicious. In my experience, when someone comes forward and begs to be spared, saying they're going to live alone, the others usually curse and swear at him, calling him a traitor and hating him even more than a true enemy."

Qing stroked his thin chin.

"Or if one person pleads for their life, the rest should all crumble. But everyone was so indifferent. You live, I'll die. That doesn't make sense."

"[No matter how incompetent they may be, they were monks who have practiced spiritual discipline. Isn't that a level of spiritual cultivation a state of accomplishment?]"

"And when you tell him to break his dantian, he immediately say, 'Yes, I will.' Does that make sense? You're supposed to resist at least once. What's the point of your dantian to someone who's not in the military? Anyway, be careful. It's like they've already decided to surrender at least one person. I think they're up to something."

This was the wisdom acquired through experience by the greatest and worst pleasure torturer in Zhongyuan, the murderer who holds the Thousand-Year-Old Castle.

One suspicious smell was so amazing that it's almost overwhelming.

"[Why wouldn't I be able to bring a crippled person, whose dantian has been destroyed by the inaction of the original monk, to the main temple? However, my admirable child, I greatly appreciate your concern. I will be sure to take care of him.]"

And then, Amukhapalap shows a Buddha-like smile that didn't match his dirty face.