\chapter{Let's Kill the Bandits (2)}

But Amukhaprap was confident.

"In the first place, there were no thieves in the West. We were the most moral people in the Three Thousand Worlds, and we do not covet other people's property."

"Eomuk Samhap wasn't a Seojangin, but a Jungwonin? He clearly followed me around like a leech, demanding I hand over my absorption magic."

"Go! The virtuous Mr. Shin was already burning in hellfire. The merit of the deceased Master belongs to everyone, and it was also the merit of the world managed by our reserve Buddhas, who possess incredible patience and exist in a world that was dangerous. I have tried so hard to rescue you, the virtuous one, from this world. Be very grateful."

"Hmm."

"You Zhongyuan bastards were already suited to our Seojang people. The most gentle and kind-hearted people on earth, with outstanding personalities. The greatest barbarians in the world. If you didn't know that crossing the Seojang land was your enlightenment, then let the empty space in your eyes replace it. Your head was just a beautiful decoration."

Haven't you seen the good people in the precinct?

Are you blinded by the fact that you only look half-and-half?

Somehow, the group was becoming more and more accustomed to Amukhaprap's speech.

But the words themselves don't seem wrong?

The chiefs I've met on my travels have been so kind and gentle, and I've even been treated with warm hospitality when I stopped by small villages or tent towns.

Of course, the generous donations also played a part.

"We must go now, you heavy butts. Endure the weight and carry it to drive out the bandits. Dinner was planned for a peaceful evening between you and me, enjoying the corpses of the bandits."

I guess it's so disheartening to hear someone say that they're going to eat dinner in hell.

"Oh. Do you have some kind of clever plan? I just can't stand to see someone acting as bait or my friends in danger."

"You were weak, fake masters with inferior skills. You lack coordination and your limbs were of different lengths, making you the same as the lame and crippled."

"Oh, why were you suddenly saying such a correct thing?"

"You, brave soul, were foolish but quick learners. Yet, you were truly a master. You, mighty soul, lead the way, slaughtering thieves. You, weak little servants, gather the bugs that flee to exterminate them."

He said he would go and kill them all, so just catch the thieves who run away.

In short, it means that they were just going to barge in.

"Huh."

And one very surprising fact.

Do the act of thinking of Qingdo!

It's a shocking, groundbreaking, and unbelievable claim that completely overturns conventional wisdom, but in reality, Qing was a despicable person who always took great care of his own safety before battle.

Even though it may seem like I'm rushing in without thinking, at least I always went in prepared with an exit plan in case things don't work out.

Of course, the enemies were always stronger than expected, or there were conspiracies such as the Blood Cult and the Demonic Cult, so it was always a struggle.

But we can't blame Qing for this.

Unless you have omniscient insight into the world, how can you anticipate and respond to others' plots?

I'm not someone with absolute memory powers, like coming from the future or remembering what I had for lunch a year ago, nor do I have the ability to read other people's minds.

"Hmm. Doesn't something seem suspicious? Even in Zhongyuan, there aren't any bandits on roads where money isn't available. Of course, it's strange for a thief to set up shop in a place like this."

"What! You said that the land of the West was a barren wasteland, a remote, impoverished, rural outskirts, a wasteland where you can wash away your eyes and find no use for a lifetime!? You should immediately kneel before the fifty million great West Leaders and apologize!"

"I didn't say anything like that."

"Robbers prey on people. The great Westerners were the most precious barbarians in the world. That alone makes a future teeming with bandits inevitable."

Qing's eyes narrow at him.

Something seems very suspicious, doesn't it?

You're being unreasonable, but was this still a trap set without giving up on the absorption magic?

If something seems suspicious, I should throw the poison bullet Nan-a gave me and run away.

Yi-mei and Sani will chase after me on their own, so I'll just take Gunyeong and my useless ornamental bamboo wife and run away.

What a truly vile and evil intention.

Qing smiled and agreed, hiding her ugly true feelings.

"Okay. Eomuk Samhap will take the lead, and we'll clean up the fleeing remnants, right?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Once you win an award, you keep winning.

Where on earth do you think the bandits are? Why were you speeding up so much? Why were you heading towards an increasingly remote and secluded part of the mountains?

He was a suspicious guy from the start.

How can you speak so awkwardly when your vocabulary was not ordinary?

Unless you're trying to be funny on purpose.

The group that left Henan headed straight east.

Although it wasn't fast, it was still running at a light speed, so Qing took a quick look at its intentions.

"Do you know where you were going?"

"There's only one spot nearby where bandits will be stationed. The geomancy of Zhongyuan was like the art of war. Seeing the enemy, approaching the enemy, fleeing from the enemy, facing the enemy, fighting the enemy. All factors were unimportant, and the place where all were aligned was called a geomantic site. There's only one such spot. If you, the valiant one, take to heart the words of your great self, you will attain the wisdom of the enlightened Buddha, unbeatable in a hundred battles."

"Isn't that the Art of War?"

"It was true that the grandson also believed in Buddha. He was ashamed of his belief in the Buddha of Zhongyuan and kept it a secret."

It's suspicious to even talk nonsense. It's suspicious.

And how could a guy who was lost and wandering know the surroundings so naturally?

Was it true that you were lost and wandering from the beginning?

Qing gently strokes my forehead.

The poison bullets I keep ready to throw at any time make their presence known with a firm touch amidst the softness.

So the group went deeper and deeper into the mountains.

The temperature has dropped sharply and it was cool.

The snow was so close in front of me, it looks like I've been climbing the mountain all along.

The terrain was rugged with low and high cliffs.

If we do this, isn't it like entering a natural labyrinth where it's difficult to find the way even if we run away?

"Is this the right place? were thieves setting up shop in such a dangerous place?"

"You were so brave. I understand that your empty mind cannot fathom the great will of the One who created it. I also pity you."

"Okay. What was it?"

"I, the master of the world's best temple, Roeumsa Temple. If you see me, you will flee in fear, urinating and swearing. Therefore, I will destroy you by surprise. The Buddha said, "Attack the enemy's rear! This was a free teaching for you, the brave one. I grant you the respect of my greatness. Shhh! Be quiet! Don't make a fuss!"

Amukhaprap, who had been talking to himself, suddenly stops and asks for silence.

If I just keep my mouth shut, it will be silence.

"There's a band of bandits coming from down the valley. From now on, we'll kill them. Once you've slaughtered the bandits, you can bypass them and catch the bugs that were trying to escape."

Qing's eyebrows twitched.

If you make a detour while attacking the enemy's rear, won't you end up blocking their front?

This guy was getting more and more suspicious.

So, Amukhaprap slowly and quietly heads towards the protruding part of the slope.

After making eye contact with the group, Qing observes the back of Amukhaprap and conveys the basic sign language of the Wulin Alliance.

There's a suspicious person ahead. Escape was possible.

The expressions of the group harden at that.

Except for Jian Buxi, who didn't understand.

So the group followed behind Amukhaprap stealthily and looked down at the protrusion of the hill.

Hmm? No thieves?

Qing'er looked at the Amukhaprap with a mixture of bewilderment and wariness.

Before I knew it, I was gripping the handle of the Moonlight Sword (10th plus).

He declared proudly,

"It wasn't this mountain."

"What?"

"I am great. But the bandits were not great. So, the location of this wonderful stronghold was something only I, who have studied the wisdom of the Buddha, understand. It was a phenomenon where the heads of foolish bandits were displayed as decorations and exist in a strange location."

The bandits have come to the best position to set up camp.

But they were more stupid than I thought, so they don't know the good spot and were probably somewhere else.

"No, really? were you going to look for them until the bandits show up? I thought you heard about their location somewhere."

"Rather, I should be grateful to myself. It's my wisdom, mercy, and fearful virtue, the great master who gave you, you lazy Zhongyuan bastards, the opportunity to train. But it wasn't just training. It was foreseeing two thieves' nests from the beginning. Only now have I pinpointed the location of the bandits."

Since I also practiced light air, it's not a loss, right?

And there's only one place for a thief to be, so he'll be there.

"Hmm. Let's go. I'm going to die like this."

And then it was straight downhill.

People in Wulin were good at running, but they were even better at jumping.

It goes down steadily, jumping over small cliffs and hills, and then at some point it goes up again, up again, up again, up again.

Qing has reasonable doubts.

Isn't this deliberately trying to drain us of energy? They're deliberately driving us up a steep mountain to make us look energetic, so they can use their energy to get us going.

And so the sun sets and disappears, casting only a faint color on the sky as if it were not yet dead.

So, it means that I ran for about two and a half hours (five hours), climbed down the mountain, and then climbed back up again.

At the end of another canyon.

The group looked down cautiously.

Hmm. Thieves? None again?

"What was it? were you sure you know the way and were on your way? There's no one here."

"Strange! Why!"

Amukhaprap looks around and shouts as if he cannot understand.

Then, all of a sudden, he clapped his hands, seemed to realize something, and shouted in an arrogant manner.

"That's right! That was the mountain I was talking about earlier!"

"There was nothing there earlier."

"Foolish! Look at that sky! It's the cunning of lighting a fire after the sun has set to hide the smoke, or the inability to avoid one's own great gaze. Surprisingly, thieves were creatures that eat!"

You made me climb another mountain because you couldn't see it with your own eyes, so what can you avoid?

If you look closely, following the finger pointed by Amukhaprap, you can see a wisp of smoke rising.

It's the mountain I came down from earlier.

"What were you going to do now that I've lost?"

"I guarantee you a dinner with the corpses of your own bandits. Also, you Zhongyuan bastards, I own a lantern. Possible."

It was a situation where Amuk Hap-rap was becoming more and more suspicious.

I thought I was wasting my energy by making him go hiking for no reason, but it's already past dinner time.

No matter how martial artists it is, if it's hungry, it can't help but be unable to exert its power.

There, at night, they didn't even remove the view.

At this point, it's not just suspicious, but there's something ulterior, and shouldn't we consider them potential enemies?

How can you believe that evil deeds were red in the first place?

"What's possible? Yi-mei, bring out the lights. Give me one fish cake and three bowls, and take the other."

"Huh? I'll just take it."

"No. This guy was coming."

Qing had a habit of his intelligence increasing rapidly only when he was very tense or hungry.

And now it was both.

If you must seal one arm of the party, it would be best to light the arm of the least helpful one.

If necessary, it can also serve as a light when carried around.

It was the same principle as handing over the light to the fish cake samhap.

Last time I saw it, it was throwing bloody handprints with both hands, but if you block it with one hand, that attack was halved.

So, in the rapidly darkening sky, two lanterns were coming down the mountain.

Towards that mountain earlier.