\chapter{Let's Kill the Bandits (1)}

The countryside on the outskirts! Henan!

There was no particular history to be proud of.

Because it has been less than three hundred years since it became the land of the country.

If you look at the person before that, he was nothing more than a barbarian, not a proud great man of Zhongyuan.

It was a so-called shit land with no particular geographical advantage, but it has developed significantly as a triangular gateway connecting Gansu and Sichuan provinces in Zhongyuan, which was why it was now prosperous.

"Hmph! The only people who were full were those ugly, hellish piglets from Zhongyuan. The precious people of the West were actually hungry."

This was the opinion of the locals, Amukhaprap.

The benefits of development were all sucked up by Zhongyuan people, so there was no benefit for the Westerners, and rather-

"These days, young people have lost their minds. They've become so obsessed with Zhongyuan style that the world's greatest Western culture was inconvenient, unattractive, uncivilized, and a world where even the most vile diseases were plentiful. We need to pluck out all of those rotten sprouts."

There it goes! 'Young people these days!'

This was an act of declaring that one has already grown old mentally, regardless of one's physical age.

Of course, this was something that even primitive people around three thousand years ago said, and it was a human instinct and a natural aging process, so it should not be hated or considered wrong.

Anyway, I heard that public sentiment was really bad before I came, and the expressions on the faces of the people coming and going were definitely dull and puffy.

Mats? Wool? Look at the gazes of the chiefs, who have gathered since morning, laying out colorful rugs and looking at the group.

His mouth was wide open, unable to close at the sight of the world's most beautiful woman, guaranteed by Jiangnan, but his eyes were hard and somehow ominous.

Of course, seeing the lama monk talking to Amukhaprap in his robes made him immediately become polite, but Qing did not miss the hostility that flashed like a spark in that brief moment.

Anyway, there was a high-class guesthouse that was built neatly, so it was called Maengchi Guesthouse.

"You guys were waiting because I received your alms. Have lunch and see you later."

"Huh? Monk, aren't you going to eat breakfast together?"

"You were a noble person. However, the opportunity to offer food to the Great One was a precious treasure that only you can enjoy. It was a perfect opportunity for you to offer food to the Great One and find joy in it. It was a precious opportunity for you to find joy in offering food to the Great One."

You're saying that offering food to me was a natural joy, but maybe that's really how the culture of the chieftain is.

It may seem strange to go around begging from house to house when there was delicious inn food, but I also think it was the attitude of a monk.

"Uh, um. Okay."

"Stay up all night and get the sleep you deserve. Kill the bandits with all your might."

You've been up all night walking, so get some sleep and rest.

It was Amukhaprap who showed great enthusiasm in suppressing the bandits.

With that, the curtain fell off, and the group went inside, removing the unique curtain of the Maengchi guesthouse.

But why was it so quiet?

Originally, when a guest comes in, the hostess should immediately greet them.

It feels good to be greeted, but it's also the basis of business.

After greeting someone, isn't it some kind of implicit social agreement to at least buy them a cup of tea before leaving, even if you don't like the store?

So, Qing looked around.

What the heck, was this a guts business?

There were no other upscale guesthouses around here, so it doesn't matter whether you go or not?

Then, the man who had been sleeping curled up at the empty first-floor table raised his head and our eyes met.

"Oh my! Welcome!!"

Qing exchanges glances with the group.

Is it okay here?

What do you mean there aren't any customers?

"customer?"

"I'm going to eat breakfast and rest. Can I take a bath?"

"Of course! Welcome! We've already filled the already clean Jaehu River with water, so we'll raise the water price by half."

"Then let's have a quick breakfast first."

"Oh, what would you like to eat? Vegetables? Meat? Rice, porridge, noodles, dumplings. Just ask."

"Oh. Um. Well, then, give me everything."

"yes?"

"Give me everything, and I'll make sure the dishes don't overlap so they're done quickly. Hmm, just five or so."

The dots were twitching and twitching.

With an expression as if he just heard something.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In fact, no matter how comfortable the sleeping arrangements are, the aftereffects of sleeping out overnight continue to accumulate in the body, especially when the weather was cold.

After all, we've just finished a arduous night march.

After eating my fill and soaking in the bath, I fell into a deep sleep in the bath without even going to bed. Then, ugh. I drank a bowl of water through my nose and gasped, "Keuk, keuk, keuk, keuk." It was like torturing myself.

And then, tired and exhausted, the most pleasant form of sleep comes over me, and as soon as I lie down, I can't even count the heat and fall into a deep sleep with my breathing ragged.

When Xue-i-ri's time came, she dug deep into my arms, but before she could even count to five, she fell back down, snoring sweetly.

Jian Buxi smiles happily, covers him with a thick blanket, and then slowly burrows into bed herself.

The sun was high in the sky, and everyone was sitting around the table in a somewhat shaky mood, as they had just been told to prepare a meal and wake up.

I slept like a log, but when I woke up in the middle of the night, everyone was still tired. If anyone saw this, they would click their tongue and wonder what the heck the so-called post-facto index of the political faction was.

The group was half-asleep and shaking, but as they started eating the food, they quickly came to their senses.

A bunch of thieves, a bunch of thieves.

Qing calls out to Jeomsoi, who was making noises in the hallway, and goes to investigate.

"Excuse me, Jeomsoi. I heard that bandits were on the rise these days?"

"Oh, it's not a big deal. This time of year should be bustling with business closing down for the year."

It's the last time the road will be blocked by ice and snow, so it's a time when people were rushing down.

However, they all chose to go north and take the long way back to the land of Seonyeong, so from late summer until now, there has been no one, so everyone has been left alone.

I recalled the first-floor scenery I saw when I came down to the separate room.

It was so deserted that only one of the four tables was eating, and the spacious first floor looked desolate.

Since there was not a single table without food or dishes, it seems that they were selling rice in a diner because there were no customers.

So, there was no choice but for the noble person who comes only a few times a year, the person who sprinkles silver like Jaesin, to be on standby.

The food was delicious, the host was very skilled, the rooms were clean, the beds were luxurious, and even the sunshades used during the day were of high quality.

The bathroom was warm and doesn't lose its heat, and the private baths were large and spacious, so it's actually superior compared to the high-end inns in the northern part of the country.

Even though Maengchi Guesthouse was a high-class guesthouse with no shortage of guests, how could it be otherwise without people?

"Those crazy bastards were demanding not just money, but people, so why don't we just cut them off? Anyway, these uncivilized barbarian bastards. We Koreans have been so gracious in helping them develop, yet they're beasts who don't even know gratitude."

The Jang people were a type of people from the western region, and were written in completely different Chinese characters than the Jang people living in Guangxi Province.

"The chieftains? were those bandits the chieftains?"

"Yes. I heard you wore the chief's uniform."

And then Jeomsoi whispers, lowering her voice.

"There must be more than a few barbarian bastards in this village to begin with."

"Hmm? Why was that?"

"Where and how would that group of thieves get food? Of course, they'd have to find somewhere to get it. And since no one in the Henan Korean Association was missing that much, it's only natural that the Jangjok bastards would provide them with food."

It feels a bit strange to hear that it's a Korean association.

I heard that the Korean community in Henan has a tight grip on the market.

If you happen to be going to Seonyeong, I will also add that I will introduce you to fellow Han Chinese people at a good price.

Those Jangjok kids were determined to put a lid on anyone they see.

"Well, that's something we'll need later. What about the bandits? were there any famous masters among them? It's been quite a while since late summer. Even if the officials were playing around, the merchants didn't even hire masters, right?"

"Would you, the masters, ever come to such a remote, rural place? Moreover, you wouldn't be able to pull a cart, so what would you do on a journey of little value? This route isn't even popular."

If it were a profitable path, the signboards would have been established and would have already made a fortune in large-scale logistics. However, why would you invite experts to a small alleyway business district in the countryside that doesn't even touch the small signboards?

If you're going to spend that money, you might as well not go.

"That's great. That expert was here."

"Oh my, Nari!"

It was Jeomsoi who suddenly fell to his knees and bowed deeply.

It seems like you've been going through a lot of mental anguish lately.

Even though they look so young at first glance, they must have bowed deeply.

"So, if you know anything, could you please tell me?"

"I'm not sure, but I think it's probably seventy li to the east, in the Geukgihyeok Valley. The barbarians call it Geihe? The barbarians call it something like that because their language was twisted. That's the only place where bandits were likely to invade."

Even if you go east, they appear like ghosts on the main road where logistics were carried out, so they must have set up shop before the road splits into north and south. Also, there were only two places where you can look down on the road from afar and go down in advance to set up shop.

Among them, the highest and closest position was Geukgihyeok, so it was obvious that he would have set up a mountain shelter there.

Or, it was the Xuetache Valley on the southern mountain range of Geukgihyeok Valley, and because the terrain was rugged and difficult to climb, even thieves would have avoided it.

"I don't know how many there are?"

"I don't know for sure. Since they've taken people, it could be quite a lot. And since there were thirty or forty people, each with different opinions, I'm guessing there were around fifty."

"Um. Let's talk amongst ourselves."

First, bite the point.

"San, what do you think? Fifty?"

"If you're just holding a knife anyway, then fifty or so won't be a big deal."

"Yeah-"

"The problem is, I don't know if there will be any experts."

Peng Daesan blocks Qing's words.

Well, I thought it would be just another pointless story about a super-climactic brat anyway.

In fact, that was actually the case.

"As Mr. Jeomsoi said earlier, it's a remote mountain valley with no roads. What kind of expert would be robbing a place like this? And what's the problem with a Strange Monk monk? Even if a true expert were to win, he'd easily win this battle. Oh, right. You might not understand if I say it this way, so I'll tell you, but if a true expert— ah, um."

Peng Daesan stuffs lamb meat into a triangle-shaped dumpling and puts it into Qing's mouth.

"Jinta Gus was a vegetable farmer, Gatta Gus was a farmer, hehe, mash it up."

It was a slurred speech in which the mouth was wide open, so the lips were pursed and the inside of the food was not visible when chewing.

It seems like the dumplings aren't that big so they don't completely block my mouth.

Qing, who had chewed and swallowed the dumplings thoroughly, stroked the back of Xue-i's head.

"What can we do, we're so weak. Just a peak. Oh my, give me the chopsticks. They're too heavy for a peak."

Xue-i-ri's eyebrows furrow slightly, and she was lost in thought about whether she should protest now or not and if she just passes the chopsticks, the food will be eaten.

Peng Daesan lets out a deep sigh.

As I was doing that, thud!

A middle-aged man appears, opening the door to a private room where others were eating, and coming in, so to speak, he was also very polite.

The fluffy hair was bluish, so the bald head of the middle class in Zhongyuan was very difficult to manage and requires a lot of care.

It's not shiny because there's no hair.

"Still eating? The children of Zhongyuan were so lazy."

"Ah. You're here for the fish cake soup? What about lunch? Should I order something?"

"It was admirable, but only the mind accepts it. I have already bestowed countless merits and brought joy to countless sentient beings. I am full even without eating, just like the mind of Siddhartha."

Then, he sits down and starts eating the leftover food, or rather, the food that he hasn't finished yet, since he doesn't leave any food behind.

What? Didn't you say you were full?

"You lazy bastards were ignorant, but you were different from me. I, the Great One, have already identified the true nature of the bandits."

"We were talking about that anyway."

"You, the brave one, will surrender without a moment's hesitation. But your slowness was like that of a snail, so open your ears and listen carefully. The true identity of the bandits."

After saying that, Amukhaprap stuffed a triangle dumpling into his mouth and started eating it.

What was it? I'll let you know later?

As everyone watched the Strange Monk chewing the dumpling, Ddaengjung swallowed it and continued speaking.

"You wicked Zhongyuan bastards! Your vile, filthy, beastly natures were only meant to harass the great Xizang! All of you bandits were Zhongyuan bastards!"

The expressions on the group's faces were like, 'Well, that's it'.

\vfill
\begin{lstlisting}
	The chapter's title is a reference to a Korean meme 'Let's kill the ants'
\end{lstlisting}