\chapter{A Cunning Mind, a Wicked Heart (2)}

Qing imagines himself carefully inserting the Palgwanpil (brush).

The sight of a manly woman punishing evildoers with a single brush, if even the enemies heard the rumor, wouldn't they tremble in fear, thinking that a ghostly woman had come and wet her pants?

Is this something I absolutely have to learn?

But, can I learn it?

"It's not really a vision, it's just a suggestion to learn a little bit. Rather, wouldn't it be a blessing if a famous person like Aga were to use the cavalry?"

In a way, it was the same logic as Ximen Surin.

Just as Qing must set an example as a master for the revival of female martial artists, wouldn't interest in Gimun weapons increase?

If you say so, then there was no reason to refuse.

but.

"Excuse me, but can I visit you after I've visited the Lord of the Eight Gates? I'm so eager to learn, it's like wildfire."

"Well, well. Anyway, that Palmunju guy, you don't have to ask him anything. He's the one who always asks when the baby was coming."

He was a guy who always carries around the words, "authentic, authentic, very authentic martial arts," so he said that he must see the recipe left behind by the great emperor Mucheon before he dies.

He was the one who kept complaining about when the Cheonhwa Sword would come.

"Oh, Heavenly Blossom Sword! You came to see Jeolgeombyeok? Yes, this way. What kind of enlightenment did the Great Emperor Mucheon gain from seeing the joint martial arts? I spend every single day pondering it, unable to even sleep."

In fact, Palmunju's reaction was like that.

Rather, it was the elder of the common faction who was trying to guide us to the cliff wall right away.

However, it was not possible to just watch the cliffhanger without any hesitation, so shouldn't the joint faction also select the spectators first?

"Ah. Right. I was being a bit scheming. I wanted to see that move before I closed my eyes. Oh, how scheming."

So, he readily asked permission from the heads of the eight gates and headed to the seven gates again.

After visiting the eight gates, I can definitely understand why the seven gates were not popular.

The eight gate gate Taegeuk gate was bustling with activity, with young and old disciples practicing together, and the shouts of "Yiyap, euryat" resonated with a great sense of energy.

Compared to that, the Chil-Gwan Gate had a quiet and desolate atmosphere.

Of course, there was also the fact that the Ki-moon weapon was not a friendly study that basically just told you to shout and attack now.

"The term 'gimun weapon' isn't really appropriate. Isn't it simply called a 'gimun' because it's not commonly used? Yes, for example, there's the chair. Chairs have been a popular weapon since ancient times."

Since Zhongyuan have been living a standing lifestyle since ancient times, the history of chairs was in line with the history of the Zhongyuan.

And when you need to beat someone up right now, what could be as easy and effective as a chair?

"There's also a weapon called the dagger. It was a popular weapon in the past, but now it's in decline and was considered a rare weapon."

I'm talking about the mortar and pestle.

The weapon I use was modified to be much more vicious than that, and it was made by connecting two iron hammers with sharp blades at the ends to the handles, and that was the weapon I call myself.

but.

From what I felt while using Qing-i Cheolchu-eonwoldo, a weapon with a cutting edge at the top and bottom and a center grip was fierce to handle.

They were the warriors of Zhongyuan who used the cosmic mystery of qi to fly, exert great strength, shoot light sabers, and even ignore the laws of nature through thought.

Simplicity was the best, but rather than holding the center and swinging it, the movement was limited, so it was bound to be naturally eliminated as martial arts develop.

"The same goes for the Hosugu. Originally, it was one of the Eighteen Weapons, a time-honored weapon of Zhongyuan, passed down from generation to generation. But how many martial artists still use the Hosugu today?"

In fact, the ball was still a powerful weapon today.

It looks like a paru in the style of Qing hometown, but its hook was a sharp blade, and the handle also has a blade to protect the hand, so it was an all-purpose weapon that can stab and cut just by holding it and imitating the martial arts.

However, it was very inconvenient to carry around.

And above all, it's not cool!

For martial artists, style was a very important matter.

There was even a saying that when a martial arts competition was held, all the dog grass in the village disappears.

I have no idea why that damn dog was carrying that weed in his mouth, or who started it.

In fact, style was not something that was important only to martial artists. In fact, the temperament of Zhongyuan people was that way.

Just like when the three forces of the above, Chok, and Gangnam Vigilantes were fighting to divide the world into three, the strategists always carried large fans in their hands.

After that, the helmets of the soldiers gradually became more intense, as if they were carving and erecting the heads of various birds high up.

"However, it's true that the power of the gimun weapon was weak. What other weapon was better than a sword, a dagger, or a spear for stabbing, cutting, and striking? But if it's a weapon everyone uses, then that's the problem. What if a swordsman encounters a swordsman superior to himself?"

When a swordsman meets a swordsman better than himself, he has no choice but to be struck by the sword and die.

It was the same for Taoist priests and Changsu.

"But what about cavalry? The enemy doesn't know how to counter it, and even if they know it through hearsay, it's not easy to handle without seeing it firsthand or facing it. That's the essence of cavalry."

"Wow! If you don't know, you have to be right!"

The cavalry officer's eyes widen at that.

If you don't know, you have to be right? It was a sweet sound I'd never heard before.

It's a wonderful and heartbreaking expression that I haven't thought of until now, after a lifetime devoted to the subject!

"Yes, that's it. Here, baby. Take this."

"Oh. Thank you."

Qing politely accepted the basket offered by the cavalryman.

And when I opened it up, Hmm? What was it?

No contents?

What does this mean? Is this an empty lunch box?

Are you really asking me to come without any preparation just because I said I would teach you?

As Qing blinked, the cavalryman let out an old man's laugh.

"Honey, that's the magic weapon."

He looks at the basket.

In Zhongyuan, it was called a ramza, and its long strings and flat shape were somehow familiar even in Qing homeland, and it was made to be worn on the shoulder or tucked at the side.

"It was also the weapon used by Nam Chae-hwa."

Nam Chae-hwa was one of the eight renowned great immortals known as the Palseon in Taoism.

He was a god with very peculiar tastes, who was said to have gone around begging while singing, dressed in women's clothing, holding a three-foot-long cane in one hand and a flower basket in the other.

However, there was no record of Nam Chae-hwa flying on a crane or hitting people with a flower basket.

However, since these were the words of the Supreme Elder of the Kongtong Sect, an orthodox Taoist sect, it seems that was how they were passed down in the Kongtong Sect.

Even so, it may be an anecdote that was secretly passed down, as it was said that if you hit someone with a flower basket, you save face as a god.

However, he was already a Namchaehwa immortal who wore women's clothes with his hair down and begged with one foot bare and one shoe on.

I wonder if there was any dignity to protect.

"It's a basket with a steel core. You can use the steel core at the bottom to strike or stab enemies, and it can also be used as a shield by twisting the wire between the warp and weft."

"oh."

When Qing finally felt under the basket, he could feel a hard, thick iron bar.

I thought it was a bit heavy somehow.

"And above all, there was a great advantage that only baskets have."

"What was that?"

"It can hold things."

"Oh! It has storage capabilities!"

Qing burst into admiration, then suddenly stopped.

This was called a basket.

Don't use it to store things.

Well, isn't that obvious?

But the true value of the basket was there.

Despite being a weapon, it was very practical?

That's not the point.

If you put something like a poison barrel in it, it becomes a basket that shoots poison needles?

That's not the case either.

The point was that no one in the world was nervous when they saw the basket.

How powerful would an unexpected move be in battle?

"The Way of the Cavalry was to transform everything you can get your hands on into a weapon. People might point fingers and curse you, calling you cowardly."

The cavalry officer smiles kindly.

"But our common ancestors bore that stigma to protect innocent civilians from their enemies. Isn't this the spirit of agreement that we will stop at nothing to punish evildoers?"

In the end, it was a statement that he was willing to die in order to win.

Isn't it true that everything depends on how you package it?

And those words resonated deeply with Qing.

Well, that's right.

Why should we be picky about the means and methods to catch those bastards?

"Okay, baby, let's get started."

In fact, the training in the martial arts class was different from what Qing had expected.

Qing's true intentions.

The great activity of the martial arts window, registering one martial art at a time, even if it was only for handling various types of magical weapons.

But the study of the common wave was not like that.

Rather than organizing it into a structured study, it was a study that analyzed the utility of things and thought about how to use them, with the goal of making everything one holds a weapon.

But it was also a truly beneficial time.

If there was a sharp part, stab it.

If there was a long part, hit it.

If there was a bent part, hang it, if it was sagging, swing it and tie it up, and if there was a part that can be hidden, hide it.

If you can sharpen it and use it as a blade, sharpen it fiercely.

This was the secret of the joint cavalry that pursues the use of the form itself rather than a standardized weapon.

Of course, it was impossible to learn such deep applications in a one-day cram class.

Especially since it's not a blue dragon without a sword.

It was like dumplings without filling, sweet and sour pork without meat, mala-tang without mala, and porridge without grains.

It meant that despite his reputation as a genius, he had no substance.

For that reason, the cavalry training ended up being an experience of being beaten by cavalry, rather than a training session for Qing cavalry.

But, if not now, would I be able to get hit by all kinds of strange weapons?

But, even though the cavalry commander called me "Aga, Aga" in a very affectionate manner, he surprisingly didn't show any concern and just passed me by.

Well, since Qing didn't show any signs of pain and was being beaten bravely, the cavalryman thought that Aga really had a strong back and beat him up hard.

If you don't know, you have to be right.

If it's right, you'll know.

What you know doesn't have to be right.

As a result, Qing has gained resistance to countless types of magical weapons!

At dusk, you will see a strange weapon with a cavalry gate and even analyze it.

What was it? The body was curved and twisted, and there was a sharp part, so if you block it, it will bend and come in and aim for the neck or armpit.

Rather than saying that I learned how to kill people with a pencil,

The result was that I developed the insight to be careful of my eyes, ears, and neck when someone stares at me with a pencil.

This is, above all, a change in perspective.

It was said that people see as much as they know.

During Qing Dynasty's beggar days, mountains and rivers were nothing more than weeds that could be eaten when hungry.

But now that I have read medical books and learned about medicinal herbs, it was the same reason why the grasslands of the mountains and rivers now look different with weeds, medicinal herbs, and wild vegetables.

This already vicious woman, she started to think that anything she saw could be used to beat and stab people!

In other words, it can be said that the cavalry general poisoned the world.
