\chapter{A Cunning Mind, a Wicked Heart (5)}

A new hole has been created in the cliff wall.

However, it was a small hole, different from the original trace of the Great Emperor Mucheon, which was a basic sword mark that had been pierced by about two fists.

Even if you look closely at the traces of the cross-section of the long moonlight sword, the other side was dark and cannot be seen like the original.

Traces of the sword losing its power and disappearing midway.

The joint-army drones were a little disappointed.

Why was it that in Shaolin, the heavens and the earth were turned upside down, and in that volcano, the flower petals of the strong energy swirled wildly like a waterspout and bloomed in full bloom?

But what it actually showed was a straight line of swords extending out without any warning.

If it was the hometown of Qing, they might have made a fuss about light cannons or destruction beams.

Unfortunately, the ancient Zhongyuan was still an uncivilized, primitive society before the development of civilization, and was thus unimaginable.

Of course, that's what they say.

Even if you visit every day and look through the hole, you cannot know the remains of the Great Emperor Mucheon.

The imposing and graceful appearance of the Cheonhwa Sword, which shows off a plausible move at a glance, was truly the future of the Jeongpa martial arts world, the pride of the Jeongpa martial arts world.

Qing was firmly encouraged.

What, the part where you can control the power?

Qing roughly estimated the true energy of Dantian.

I had done nothing else, so I was fully charged, or in short, fully charged, and was heading to the cliff.

Judging by the state of his dantian, it seems that he consumed roughly one-third of his internal energy with this single attack.

Of course, in return, the power was greatly reduced.

Compared to the original herbivore, it was nothing more than a mere imitation that was embarrassing to call the same herbivore.

If I had to say, it would be more accurate to call it a simplified or deteriorated version of power control.

Right now, the best I could do without damaging my body was at this level.

This meant that the gap between the Emperor Mucheon and Qing was this great.

But, I rather like it.

That is, it meant that all of the energy would no longer be consumed in one go like before, and the aftermath would not cause massive damage to the energy pulse.

And as if that wasn't enough, it was the power of a blue dragon that was beyond human power, squeezing muscles and bones.

It also means that it won't happen, as I used to collapse with muscle ruptures and compound fractures all over my body.

By the way, why?

That's because my understanding of vegetarianism has increased, and my understanding of my body has also increased.

I have a vague feeling that I can use my body to its fullest potential without harming it, and although I can't explain it in words, I do know that I can.

I feel like I'm finally a real expert.

The original expert does not know the details.

Only less expert people know the details.

So, if you ask a true expert, wouldn't this be the answer you get?

Oh, that's, that's just how it is. It's just like that. What was it? There's something about it, and that's why. That? You just have to get used to it, right?

Only less expert people can add detailed explanations using all their specialized knowledge.

Qingdo was now a mid-level martial arts expert, so, um, that's possible, but I don't know how to explain it, but in that state.

Or maybe it was because he had now mastered all three of Dokgogugeom's first three techniques.

Wouldn't the first half of the original course be the introductory stage, where it serves to lay the most basic images and foundations?

Now that I understand the sincerity with which the Great Emperor Mucheon treated Dokgo Gugeom, and his obsession with martial arts, this method becomes clearer to me.

So, it could be that I can use it as my own custom.

Or maybe it was possible from the beginning, but that damned Emperor MuQing interfered.

In fact, how can a person ruin his body by eating herbs?

Even though Qing's internal energy was said to be of a high level, I wonder if it was not at a level that was sufficient to use the Dokgogu Sword.

There may have been some interference, some forced help from the inner world of the mind.

"Oh, what is this Movement?"

"It's the Third Movement, Wicked Heart. I lack the skill to execute it perfectly, but it's a technique that allows for a surprising attack."

"Wicked Heart!"

Jang Pa-in bursts into admiration.

A word that truly suits the spirit of communism, a word that seems to have been created for communism.

"Martial arts were a means to murder, and human nature was cunning and vicious, so when they gain power, they wield it to harm others."

It was the image that Mucheon Daeje contained.

That was why this vicious surprise attack technique was placed right in the place of humans, humans among all of heaven, earth, and humanity.

It was not the place of a human being, but this kind of surprise attack and the viciousness of not hesitating to pierce the enemy's heart that was the very essence of humanity.

But this was not a criticism of people.

It was not a justification that it was natural for a person to study martial arts and kill people with his skills.

How can we say that it was man's fault that his innate nature was cunning and his heart was vicious?

Rather, I must be conscious of this and keep in mind that I am ultimately only human.

Because the poison-free chieftain was this herbivore.

Because Samchosik was waiting behind him.

Three herbs, three kinds of herbs.

Where you were was the center of the world.

Only by acknowledging that I harbor a demon within me and not denying it can I truly stand on my feet and reach the earth.

"This was the teaching of Bokma."

"It seems that the Great Emperor Mucheon was quite pleased with Kongtong's martial arts."

"Yeah. That's what it looks like."

Jang Pa-in smiles broadly.

The communal ignorance was criticized as being too life-like and overly bizarre.

It was also a concern that the common disciples who claimed to be orthodox Taoists always had in their hearts.

Wasn't this the support and recognition that the greatest warrior of all time was sending him?

On the one hand, aren't you avoiding and avoiding the essence of learning martial arts to wield weapons and harm your enemies, while being too obsessed with the appearance of a Taoist?

Perhaps that was why, here and there, people who were sitting cross-legged and slumped down start to appear one after another.

Emperor Mucheon was the most far-reaching warrior in history, and his convictions were so persuasive that I find myself unconsciously accepting them, and they give me the confidence that I am on the right path.

And because it was what was most needed by those who were always wandering on the path of ignorance, not knowing what lies ahead.

The joint forces of the side that had not found any clues looked at each other with regretful eyes, held their weapons, held their breath, and assumed a posture of protection.

So what? Outsiders have to go back.

Now that even a single word can be a nuisance, Jang Pa-in shows his gratitude by taking a punch.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A series of very steep slopes opened up in the common area.

Compared to the fact that the common shamans were said to be masters of battle, the number of masters was very small, so it was an even more joyful and double celebration.

So, it was only natural that all the Taoist priests of the Kongtong Sect faction gather together on the way to see off Qing.

The communist party members, including Jang Pa-in, were angry and urged to stay longer, saying that today was a memorial service for who, tomorrow was who, and the sand was who.

But there was no reason to leave your home and settle down in someone else's sect, right?

Qingdo Qing has achieved great results in his own way, but it's not like he's suffering from a complex injury like before.

So, let's go.

Kongtong Sect was the border itself that divided Gansu and Shaanxi provinces, so if you exit the main gate of Kongtong Sect and descend along the mountain path properly, you will reach Shaanxi.

Although Kongtong Sect belonged to Gansu Province, it was actually much closer to Shaanxi Province, and even when comparing the provincial capitals, it was closer to Xi'an (Chang'an) than to Lanzhou.

Pyeongnyang, a moderately large city located in front of Kongtongsan Mountain, was the upper reaches of the Geumha River.

It was a large stream that reached the forbidden Seoan and merged with the Hoeha River, meaning that there was a direct waterway to Chang'an.

Unfortunately, Qing's Dragon King Seal was only for the Yangtze River, so it was not applicable to the Jin River, which connects to the Huai River.

So, it was impossible to declare that if you light me up with the Dragon King's Badge like before, I would give you the opportunity to enjoy the powerful power of tax exemption.

But even without the Dragon King's Seal, look at the faces of the group.

Qing was rich.

She was much richer than she knew.

Peng Daesan was also rich.

He was a son of a very wealthy family who has never once been short on money.

Even Jian Buxi was rich.

Whenever she went to Jianghu, you can immediately withdraw money in the name of several superiors, and even if you don't, if you take on the role of a servant of Qing, the voucher book that Choi Riong usually gives you was a primitive ancient blank check book that allows unlimited withdrawals.

And even if you have this as a backbone, it was certain that you will never be short of money in life.

Of course, Xue-i-ri was a dog, but it's not surprising.

So, it was Qing who confidently walked towards the ultra-luxurious cruise ship that was obviously in good condition.

"Huh? There's no room? Hmm, did the people of Zhongyuan live this well?"

Well, if they were traveling around Zhongyuan, aren't they usually well off?

Look at the conditions of travelers in this era.

Even if you were away, your business should run smoothly and your assets should remain intact.

And isn't it a harsh world of martial arts, with ferocious and dangerous beasts and even more dangerous humans?

So, you must have the financial ability to hire bodyguards to protect your body.

The term 'beggar' refers to a poor traveler or a vagabond, so being a traveler was originally a privilege only the wealthy could have.

People who can afford to ride a three-story luxury cruise ship don't necessarily postpone their schedules to earn a few gold coins.

But it's a bit of a waste to bet a lot of money.

You could just take a carriage, but taking a boat was more convenient and faster, but not quite that far.

dinghy?

A small boat was uncomfortable and dangerous, so it's much better to just take a carriage.

It was when Qing was about to turn around with a regretful expression on her face.

Someone rushes out and grabs Qing.

"No! Miss? Aren't you a miss!?"

"Hmm? Do you know me?"

"Oh, my name was Namsol, a member of the TaeQing Sangbang. Please just call me Namga."

"Ah, you were the TaeQing Sangbang."

"Oh, please speak freely. How could something so lowly dare to receive the respect of your majesty?"

"But."

"Please, it was my lifelong wish!"

Hmm.

If you're talking about TaeQing Sangbang, isn't that the Sangbang that my grandfather established? Or was it not established by my grandfather, but rather occupied some other important position?

Anyway, maybe because of that, the people of TaeQingsangbang tended to be overly humble.

This was also the case with Xuega Sanghoe, a joint venture between Xuega and his grandfather, but TaeQing Sangbang was much more, how should I put it, cowardly?

Grandpa, I think this was really teasing the employees.

Of course, it would have been a bit unfair for the TaeQing Sangbang employees to hear this.

The reason I feel a little wronged was because I want to be mean, so even if I have to endure the injustice, I want to be treated comfortably.

"Are you heading to Xi'an? If so, I'd like to invite you aboard our ship. No, it would be an honor for me to be allowed to do so."

"Huh. They just said there was no room-"

Qing stopped talking like that.

The sailor who said there was no room was now stuck to the floor, his forehead and entire limbs exposed. This was the so-called prostration posture, with his forehead, arms, and legs pressed against the floor.

"No, what was this?"

"Even with my eyes, I, a lowly servant, could not recognize you. If you permit me, I will pluck out both my eyes as an atonement!"

In Zhongyuan, gold was nothing more than a second-rate means.

The best and most effective tool in Zhongyuan was connections.

That is, it was in a relationship!

"No, of course I said there wasn't room, right? Some people have room, others don't. Why were you prostrating yourself and apologizing when you're just doing what you should have done? Now, please stand up."

"Ah, how merciful you are…. Such warm mercy like the sun…."

Qing sighed deeply at that.

These damn bastards were real.

It's to the point where I have a reasonable suspicion that if I say even one good word, I'll suddenly get 10,000 points on my performance evaluation and be promoted to a good position.

Honestly, I think it would be quite possible for a grandfather to do that.