\chapter{A Cunning Mind, a Wicked Heart (1)}

At one time, Kongtong Sect was famous as the best sect in the world, surpassing Shaolin.

May Baek-i leave behind a poem-

The world knows our collective courage, and our spirit was as fierce as the autumn wind.

The descendants of heroes will continue, and their spirit will remain strong for a hundred generations.

Du Fu also left behind a poem -

If you take up a sword to protect yourself, you should go up to the common and ask for instruction.

The two-horse carriage that led Zhongyuan poetry, Li Bai and Du Fu, both wrote poems and left behind the dignity of the common school.

But! Amazing fact!

The founder of the Kongtong Sect, Zhenren Bihongja, was actually a monk of the Shaolin sect (roughly the original ancient Shaolin Temple)!

This was the reason why the Kongtong Sect was a Taoist sect, but also had a very strong Buddhist scent.

And since they were the only martial arts schools in the world, this was also the reason why Shaolin Temple can boast that all the martial arts in the world came from them.

Of course, if we really want to be specific, Shaolin's martial arts originated from India, so it would be right to say that all martial arts originated from India.

So, was the best sect in the world Shaolin Temple or Kongtong Sect?

Strictly speaking, both were correct.

The common people were experts in war.

The common mountain has been a border since ancient times.

This continued until the end of the previous dynasty when the Western Zhou voluntarily surrendered the land of Qinghai, so the history of the Kongtong faction was a history of fighting against foreign enemies and being the guardians of the western border of Zhongyuan.

Thanks to this, there were eight steles erected in the public domain, gifted by the emperors of past dynasties to commemorate their protection of the country.

This was also the reason why Li Bai and Du Fu left behind poems praising the Gongtongpa, leaving Shaolin aside.

Even among those recorded in history books, there were records of the Kongtong Sect repelling barbarians and saving tens of thousands of lives, and these were handed down from era to era.

Of course, half of them were armed groups called communists before the communist dictatorship, but anyway.

So, in terms of group tactics and warfare that operates as a single army rather than ignorance, the common faction was truly unrivaled.

However, because it was closer to military studies than martial arts, the depth of martial arts itself was evaluated as shallow.

If I were to summarize it in one line, it would be that they were scary when they gather together in a group, but they were nothing special individually.

"Jang Pa-in, how have you been?"

"Hmm. Right. How's Heavenly Blossom Sword doing? Your beauty was blossoming with each passing day. If I don't expel you quickly, all the sons of the clan will fall ill with grief. And you, too, Jade Kirin. Oh, you came here to bring the clan's daughters to bed with you?"

The joint wave long wave, Park Du-gu, a short iron man, throws a joke.

However, since he has a very serious expression, it was hard to tell if this was a joke or not.

For reference, the nickname of the ironsmith, Park Du-gu's Gu-hook, was a type of iron weapon, and refers to a heavy hook made of iron.

It was the very thing that was called Paru in Qing homeland.

Parkdu means to break the head, so Parura, meaning to break the head, was a very vicious nickname.

"Hehe, I'm on my way back from seeing the cliffs in Kunlun."

"A cliffhanger! Yes. Now that I think about it, you were a thief who came to steal our shared study. Hmm. Hmm. Hmm."

He was a slacker who kept making old jokes.

And then he pretends to clear his throat and then asks quietly.

"By the way, how old was Kunlun?"

"It was a three-course meal."

"okay?"

A faint smile spread across Dancheolja's stern face.

Qing continued speaking to him cautiously.

"That, the Great Emperor Mucheon's will? His thoughts? The spirit he left behind in his martial arts? I had a conversation with something akin to a ghost, and it seems he left this recipe in the Kongtong Sect…"

He was the Great Emperor Mucheon who was treated as an evil spirit.

Although it wasn't directly stated that this herb was in the common area, it was probably this herb since they told us to go there next.

If this recipe was right, you won't be disappointed by getting your hopes up for nothing, and if it's wrong, it'll be a surprise gift.

I thought it would be better to tell you in advance.

"I see……"

The ironsmith's face became solemn again.

But that was only for a moment.

"The first was Shaolin, the second was Kongtong. The third was Kunlun? It seems like they've been going through the orthodox sects in that order. The fourth was either Amipa or Wudangpa."

This seems to be referring to the fact that the five great martial arts schools of Zhongyuan were Shaolin, Kongtong, Kunlun, Ami, and Mudang. Could it be said that he was a person with a truly positive mindset?

Well, since the shaman said it was a herbivore, I don't think it's necessarily like that.

"By the way, Kunlun. A letter arrived asking us to prepare for support in Kunlun with a large amount of money. What on earth was going on?"

For reference, the term "대지급大至急" means that it was a matter that must be dealt with with the utmost urgency.

Qing readily confesses to him what happened in Kunlun.

Since I was going to receive it through messengers anyway, I was also given the task of delivering news on the way to provide joint support in case something big happened.

"Huh, those Blood Cult guys. Still, from what I've heard, it seems like the issue was almost resolved. With our seniors here, those bastards wouldn't dare set up shop. Yeah, that kid. Hmm."

Dancheolja's gaze, looking at Ciyu, who had fallen into a deep sleep in Qing's arms, was filled with pity.

In fact, since they were true masters, whether it was Qing or Dancheol, they could tell whether a little kid was sleeping or not just by feeling his presence.

When my story came up, I pretended to sleep quietly. Perhaps it was a desperate but desperate tactic, hoping that if I pretended to sleep, my story would come out honestly.

"Heavenly Blossom Sword has made a truly difficult decision at such a young age. It would be a lie to say I'm not concerned, given his dark side, but it does show that your seniors have great faith in you. However, taking care of people was the most responsible of all, and you must deeply understand this."

"Don't worry. Even if Ciyu abandons me, I won't abandon Ciyu."

At Qing's answer, the child's body leans forward, fully putting its weight on him.

In fact, what Qing said was Jo-jeok's words, so he was telling her not to worry, but he was also saying something that really worried her.

That means it was a joke that the ironsmith liked.

"Haha, Heavenly Blossom Sword was truly clever! Yeah, raising a child was doubly difficult."

Compared to that, Dancheolja's jokes were a bit lacking.

Still, Qing tried to satisfy both the public and the private sector by pretending to laugh.

Because power originally had the magical power to make even a boring joke funny.

"But, um. It's a cliffhanger. If I had my way, I'd take him there right away and show him. However, the operation of the main text isn't up to me alone, so I can't make that decision alone."

The Kongtong Sect was unique in that it calls the leader of the sect "Jangpain" rather than "Jangmunin."

This was not a superficial name change to differentiate itself from other sects.

Because the common faction originally had eight training gates called the common eight gates, and the head of each gate was already called the long gate person.

So, it meant that he was a person representing the eight long-legged people.

These eight training gates were not horizontal but vertical in structure, and only after achieving basic skills in the first gate, Biryong Gate, can one enter the Chuhon Gate, which was the gate, and move on to higher-level martial arts.

Qing blinked her eyes at him.

Didn't you clearly suggest that we stop by the Kongtong Sect and go home during the Yongbong branch meeting?

I thought you would be happy to show it to me?

Then, a smile appears again at the solemnity of the ironsmith.

"It's not that I can't. But it's a major decision for the sect, and if I unilaterally manipulate it, even minor grievances will pile up. It's just that people's feelings were hurt by minor things, and they build up into major resentments. While major mistakes can be forgiven and resolved, isn't it the minor things that were the most fearful?"

He has the demeanor of a general, but he talks like a proper Taoist priest, so it seems a bit out of place.

"Heavenly Blossom Sword, you just need to do some legwork. Jangpa asked for permission from the Eight Gates, so if you sell my name, they'll all nod in agreement, so you can go and see. Anyway, too many captains spoil the broth, and with nine of those farting idiots in one sect, we're practically on top of the mountain."

It was still a joke that was considered unpopular.

but.

"Hehe."

The girl who was pretending to be asleep couldn't hold it in any longer and burst out laughing.

I would say it was a joke that was just right for an eight-year-old (estimated).

First, get some rest.

Fortunately, Ciyu liked water.

It's not that I'm not clean, but I'm quite picky, so I don't think I'd be averse to having something dirty on my body.

Qing thinks that the Blood Cult members left the child in a dirty state, and that's why he was so filthy.

So, when it comes to taking a bath, the eyes immediately light up, and the childish side of an adult who enjoys dozing off while supporting himself in hot water has developed.

By the way, whenever Ciyu asked something, he would immediately run to Jian Buxi and show her the area he was bitten by.

Hmm. But what on earth does Gunyeong do?

Should I revoke my mother's qualifications?

Anyway, since the sun had set, I decided to get rid of the little hangover I had accumulated from the comfortable carriage ride.

The next morning, Qing set out on a tour of the eight gates, led by the Taoist priest Myeonak.

The first gate of the Kongtong Sectlmun, Biryongmun.

The Biryongmun was the most basic of the basics, teaching a total of fifteen types of Biryong martial arts, including the Biryong Sword, Biryong Spear, Biryong Sword, etc.

What's unique was that more than half of the fifteen were unique weapons, or magical weapons.

What was especially impressive was the double-sided.

A martial art that involves swinging two whips?

I've never heard or seen anything like this.

"Are you curious?"

"Yes, but was there a reason they're twins? You can hold another weapon in one hand."

Then, Biryongjangmun smiled brightly and said.

"That's why it's a pair. Once you master both your right and left hands, you can use whatever you can get your hands on."

In other words, the common faction's ignorance pursued extreme practicality.

Where can you get decent weapons in a time of war?

So, I learn everything and just use whatever I can get my hands on.

Since you can use whatever you pick up, you don't have to be stingy with throwing or breaking weapons.

In addition, he carries and swings a unique weapon, making it difficult for enemies to deal with.

In addition to that, there were many other dragon-like martial arts.

Biryongryun, who uses a round blade called Lyeon, Biryongpil, who uses a short needle disguised as a brush called Pan-gwanpil, and Biryongseon, who wields an iron fan. Etc.

And there was also a weapon called San-kun, which was a shovel with a sharpened tip that swings like a Biryongsan.

"Well, Jangpa asked me to ask for permission from the Palmunjangmun. I don't know how grateful I am for saving face like this. I will consent."

As Jang Pa-in said, it was more like a traveling performance just for fun, so Biryongjangmun gave an immediate reply without even the slightest delay.

And this door, the marriage proposal door.

If Biryonggong was a process of learning the basic operation of all kinds of weapons while staying in place, Chuhongong was now a process of freely handling them while moving around in combination with both bomdo and shindo.

The disciple who reaches this gate will now be able to introduce the martial arts he has learned as Chuhon-gong, not Biryong-gong.

Three gates, the gate of Talmyeong.

Once the fifteen weapons were almost completely handed over without any mistakes while moving, it was time to teach them how to kill the enemy in earnest.

A disciple who reaches the third gate can call his martial arts as Talmyeonggong.

By the way, the Chinese characters were different from the sword that Qing learned.

Qing Sword of Escape was a sword that allows one to escape from fate by wearing a mask.

The common sword of stealing was a sword that took the life of an opponent by wearing a mask, that is, a sword of death.

Four doors, four gates.

In the martial arts, you learn and master two new techniques: the martial arts of …

Originally, the act of rolling on the floor was considered a humiliating act for a warrior, but this was not the case for the warriors of the communist faction.

For the joint force unmanned forces that pursue real combat, fighting can be a bit of a struggle and even a humiliation.

If you win, it will be an honor no matter what, he said.

By the way, the word drunkenness was drunkenness, and the movement that feels like being drunk was considered the best, so the word drunkenness flashed through Qing's mind.

Actually, that's right, drunkenness.

When it comes to the four gates, it was possible to call a disciple who has lost his mind a "Chwigong", but it was said that it was rare for a disciple to be called that way, perhaps because it was not cool.

Five gates. Four gates, the gate of the painter. / Six gates, the gate of the painter.

A disciple of the common school could choose to learn from either the five or six gates, or both.

Both gates add a layer of deception and trickery to make your attacks more sophisticated, so you can choose whichever you prefer.

However, the martial arts line of the Shin Kwon Moon was bold and generous, so it was usually directed towards male disciples.

On the other hand, the Hwagmun was a gateway for female disciples because of its flowing and soft lines.

This was the sixth gate.

The structure was such that if you passed through the six gates, you would be able to raise all of the common basic skills to the highest level.

And then you will be given the opportunity to enter the Seven Gates and the Eight Gates, so you can either enter the Seven Gates or the Eight Gates or both, or you can go back to the Six Gates from the beginning and practice more deeply.

Now, free practice was possible.

Seven gates, cavalry gate!

As you can tell from the name, the Cavalry School focuses on training in Cavalry weapons.

A basket with an iron core, a sickle, a pitchfork, a flail, a seal (the one used for stamping), a bell, a wooden fish, a rope, a hammer and nails, a fishing rod, a bell, a belt, a double-edged shield(?), bracelets, etc… … .

Coming here was a gateway to learning, researching, and developing ways to use all sorts of junk as weapons, to the point where you'd be bewildered as to what wasn't a weapon.

And the eight gates, the Hyeon Gong Taegeuk Gate!

Originally, it was a gateway where only long-distance people could enter and learn the vision of the common people.

However, in order to compensate for the weakness of being only good at catching and weak at orthodox martial arts, it was reorganized into a gateway to developing the school's new martial arts by adding depth to martial arts.

When you reach the eight gates, you add that idea to the basic skills you have learned and were reborn as a new skill of the common wave.

If you have passed the six gates and mastered the divine sword, you can come to the eight gates and be reborn as the Bokma sword. That was the structure.

Thus, after completing three years of training at the Eight Gates, only then can one boast of having mastered the divine techniques of the Kongtong Sect.

Bokmageom, Chilsangkwon, Hyeol-eumbijo, Tongcheonjang, etc.

Perhaps that's why the cavalry commander seemed to have many complaints.

"That's why these days, kids don't really go to the cavalry school. Hey, the common foundation lies in this cavalry weapon. Everyone just shows off and hangs around the eight gates, saying they want to learn the Bokma Sword."

"But this looks much more fun, doesn't it? If it were me, I'd probably start with Chilmun."

The cavalry officer's eyes stretch out to the left and right.

But Qing was sincere, and the old man, who had been a master of the previous generation, quickly recognized him.

The expression on the cavalryman's face brightened.

"Yes, you know very well, my child. Yes, you're right. What fun was there in swinging around a sword, a spear, a sword—the weapons everyone else uses?"

And then he asks with a pleased smile.

"Now that we're on the subject, since you're a guest at Chilmun, why don't you try out a few tricks?"
