\chapter{A Cunning Mind, a Wicked Heart (3)}

The most impressive weapon in today's class was bamboo.

It's not a bamboo spear, it's literally bamboo.

It was a form in which only the ends of bamboo branches were sharply cut without cutting them off, and was called a wolf's lance.

It was said to be an ancient primitive weapon that was surprisingly useful in countless battles, and was currently being used with great acclaim by the country's military.

The leaves obstruct the view and the branches block the blade, so it was truly a battle of offense and defense.

However, there was a minor drawback that it was the same even from the standpoint of swinging a lance, but even the same weapon can be different when used by a skilled player.

It was said that after a vicious modification that adds additional blades to the outstretched branches, it can be reborn as a very powerful ultimate weapon.

Above all, it was easy to make.

Just cut the top and bottom of the bamboo and you're done.

The reason why Qing was so impressive was because it had similar power even without bamboo.

So, unlike the barren mountains and fields of the desolate plateau, when I saw the lush forests of Zhongyuan, I thought, Hmm, that branch looks useful.

If you stab me, it'll be really rough.

Such vicious thoughts, in a way, could be said to be a clear implementation of the spirit of Gimun, which was to weaponize all things.

I had just returned to the guest house after completing a rewarding and meaningful training session.

Two people who were standing right next to each other in the guest house courtyard and one person who was wandering around for no reason were caught in Qing's sight at the same time.

The ones who were attached were Ciyu and Paengdaesan, and Xue-i-ri, who seems to be out of place, was standing awkwardly in the middle, feeling left out.

What was this sight?

Could it be that you, Peng Daesan, seduced a young brat with such a smooth face!?

Come to think of it, mountains seem like they would be completely detrimental to a child's education.

Once you get used to the mountain, the faces of the men in the world will almost look like dried squid or fresh cuttlefish.

Shouldn't we isolate the mountain a bit so that the eyes don't run to the top of the head and ascend to the sky, looking down like the stars in the night sky?

"What was it? Men and women should not sit together under the age of seven. The most severe law in the world was that men and women were separate."

Then Ciyu's head suddenly turns.

Wouldn't Odo run at you, kicking his short legs vigorously?

Qing opened her arms wide to welcome Ciyu, but the girl, who was always on guard, stopped just before the collision and looked up timidly.

If a child was like a child, he should have just done a hearty body slam. Who killed our child like this?

Then a small hand tugged at Qing's sleeve.

You could have held my hand, but the way you timidly pulled my sleeve made me think, Hmm, I still have a long way to go.

"why?"

But should we say that the act of pulling someone over and telling them to come here was a step forward?

As I pretended not to be able to resist and was dragged away, Ciyu sat me down on the veranda of the guest room and took out a yellow piece of paper and spread it out.

And then he starts to write something that resembles letters by roughly holding the brush in his fist.

Father, mother, male, female, family.

It seems like he wanted to brag about memorizing the letters.

Qing was shocked.

"Oh my goodness, six letters? Damn it, Ximenja, were you really the fin-de-siècle genius?"

When Qing hugged Ciyu tightly, she let out a "hihi", and although it was a child's laugh, it was a bit gloomy, but whatever.

Now that I look at it, the floor was covered in traces of writing, so it seems that Paengdaesan was writing letters to Ciyu.

However, if the child had been able to memorize it just by writing it down, he would have already read the Thousand Character Classic.

Isn't he the great genius who teaches ten things, learns one thing, and then forgets it the next day as if it never happened?

How about six letters?

Is there something like the educational method of Pangga Vision?

"What, San? I didn't know you were so knowledgeable about children's education. How did you manage to teach our Dol-dae six letters?"

"Huh. It's the teacher's difference."

"I'm a graduate of the Hanrim Academy, right? San wasn't even a bookworm, and I'm at a decent level among the dumbest people."

"What does the book apple mean?"

"Is it true that they were like Zhuge Liang or Nan-a, who rely only on their brains but lack personal military power? Is that Sima Young Lady also from that group?"

Peng Daesan thought of the three people and quickly came to a conclusion.

"Just make sure you're on the stupid side."

"If you're in good health, your head was at ease, right? It's not because you're in bad health that you use your head."

"No, what was that?"

Peng Daesan was speechless at the sound of his brain stopping.

What the heck was this nonsense?

"Okay. So what did you do? How on earth did you manage to teach six letters a day? Are you a handsome guy? Did you do something like making eye contact while memorizing letters?"

"I didn't do anything in particular."

It was Pang Dae-san who vehemently denied any special secret to raising children.

Qing turned his head and looked at Xue-i-ri.

"that's right?"

"no."

"then?"

"There was a lot of talk."

"Huh? San?"

"Even the quiet voice pretends to be kind."

Listening to Xue-i-ri's story, Qing thought for a moment.

It seems like Gunyeong's speech was becoming more and more childish, and he's not even using his own name anymore, so he's at a loss?

A woman in her twenties was like this?

Should this be banned by national law?

Of course, it was forgivable because she was pretty.

Qing sends a questioning look to Paengdaesan again.

In fact, one of the most common prejudices against the Habuk Peng family was that the descendants of the Peng family were naturally strong and healthy, but had a dull head.

In Habukpengga, it was dismissed as nonsense and slander.

Actually, that wasn't so wrong.

The children of the famous Zhuge Liang and Sima Liang were able to recite books fluently before they were even ten years old, and Nan-Gong, Murong, and Yan Liang were famous for their literary and martial arts skills, and were evaluated as having strong bodies and bright minds.

Compared to him, the rumor that Pengga was ignorant has been going on for quite some time.

Just as the saying goes, "Can smoke come out of an unlit chimney?", a saying that has been around for a long time also means that it has its own basis.

Of course, that was true among the prestigious families of Zhongyuan.

Just because Pangga was ignorant doesn't mean you should compare him to the children of the neighborhood brothels.

For reference, the families of the 10th generation who were considered ignorant include the Hwangbo family and the Black Dragon family in addition to the Habuk Peng family.

Peng's position on this was firm.

He was not stupid, but he was brave and has a quick temper, so he does not have much interest in learning.

In other words, it's not that my child was stupid, it's just that he doesn't study.

As almost all parents claim, anyway.

So, the Peng family had been pondering for a long time how to educate their children, and the guidelines for children's education that they had accumulated in this way were passed down as the family's vision.

So-called easy and fun way to study letters!

"It's hard to explain. I'm just doing what I was taught. There aren't any specific guidelines."

"Hmm. They say even a snail can roll."

Even though he had taught him well, Pang Dae-san suddenly became a slowpoke and wiggled his eyebrows.

But what was truly surprising was this.

Should I really just sit down and relax for a bit?

Honestly, if there was a girl at the shrine gate, wouldn't it be obvious that everyone would line up to get a number and play?

Whether it's writing or martial arts, it seems like there won't be an environment for learning at all.

Mencius's father moved three times to teach Mencius and eventually produced a great sage. Why can't I just put a steel plate on my face and crush it a little?

Then, a thought suddenly occurred to me.

Then, isn't it okay if it's not a penguin?

If you go to Jegal's and sit down for a bit, um, no, it's a bit awkward for Ciyu to be next to Hyang.

Unless you're going to kill the baby.

Anyway, I think it's something worth thinking about seriously.

I thought, "Shouldn't you have some friends your own age?"

The next day was a day for Qing to see the cliff walls, and for the Kongtong Sect warriors to see the demonstration of Mucheon Daeje's herbivore skills.

But somehow, the schedule was quite slow, so we're going to go see it at sunset before dinner.

So, until then, I tried to sneak a peek at Peng Daesan's children's education and learn a little bit.

"Hmm."

"why?"

"Hmm."

According to Xue-i-ri's testimony, Pangdae-san began telling stories from the past in a gentle voice, and at some point, he naturally switched to writing, drawing her attention.

However, for some reason, he just keeps showing a blank, uncomfortable expression.

He looked embarrassed because someone was watching him.

So what?

You can't afford to miss out on the miraculous achievement of memorizing six letters a day.

I have no choice but to leave the seat.

-is, a lie.

After leaving the guest room, Qing hides in a tree far away and uncovers the truth about eye-level education.

Such superhuman eyesight and hearing finally capture the essence of that gentle, refreshing smile and that deep, infrasounding voice that blooms on that smooth face.

But, um.

Wow, it's so rich. It's like I just drank a bowl of sesame oil.

I think I know why you were embarrassed.

My hands and feet were curled up so much that it's hard to watch.

But what I see was embarrassing, and does it not matter if Gunyeong was hanging around Ciyu?

Are you treating me like I'm practically a nobody?

Both the mountain and the wild.

Then, when his concentration wavers a little, he runs to Jian Buxi and hugs her, and then Yi-mei walks around holding the child.

Xue-i-ri was also standing in an awkward position, doing nothing.

Hmm. What exactly was Gunyeong's role?

I'm trying to get closer to him, but he's just right next to me.

After lunch, the extremely delinquent parent who was starting his afternoon observation suddenly nodded.

Well, I'm a little sleepy after eating lunch…

In the end, Qing managed to hug the stump tightly and fall into a nap on the tree.

As the place was not as cramped as it was during the Kunlun period, the group, along with the crowd of Kongtong Sect warriors, followed behind them as they headed towards the cliffs behind Kongtongsan Mountain.

Qing's impressions after seeing the cliff.

Hmm. Something. It's really small.

It was at the bottom of the cliff, roughly the height of a person's forehead.

A hole the size of two fists was gaping.

Compared to the cliff walls we've seen so far, it was a very simple structure.

What was the absolute wall?

It was vivid evidence of the massive destruction of nature and the environmental destruction committed by Emperor Mucheon, with a huge sword scratching the cliff, leaving a large scar.

But, E-gye, a hole?

I'll drill a hole about two fists in diameter.

It was when Qing was trying hard to hide her disappointment.

Suddenly, a faint red light appears in the hole.

And then I realized why I waited until sunset to climb the cliff.

This hole was wide open all the way to the other side.

When Qing bent down to adjust the height, the sun setting on the other side of the hole, barely visible, caught the image of the hollow mountain hanging over it perfectly.

No, what was it?

What do you do when you dig a cave in a mountain with swordsmanship?

Since the Great Emperor Mucheon (original) only released one herb, doesn't that mean he went through the cliff in one go and reached the other side?

If it were the size of two hearts at once, wouldn't a cave that goes through a mountain be dug out with roughly two or three hundred repetitions?

If he had been a carpenter instead of a warrior, he could have been in charge of civil engineering in this ancient Central Plain.

No, if it's a construction project like building a road in a mountain, it would be on a scale that could almost be called historic.

Just as the person who built a dam on a river in the past was revered as a god of water control, I wonder if the god of construction will be worshipped as a god of water control by setting up shrines here and there, and if he was not at the level of a Taoist immortal.

That was the moment.

There was a loud kick to Qing's huge butt, and Qing fell over, then flew up and stood looking back.

"Miss. What was it? Now you're hitting people too?"

"Huh. I was so shocked to see a grown woman sitting with her butt sticking out in front of an adult without even knowing it was shameful."

The Great Emperor Mucheon snorts, "Huh."

"I've seen all sorts of things in my life. What kind of nonsense was that?"

But Qing feels wronged.

Well, I bent down to look into a hole the height of my forehead.

Isn't it natural for a woman's butt to fall backwards when she bends over because of the center of gravity of her pelvis?

And why did you show up from behind and then stick your butt out to me?

If you think about it, he dug the hole himself, so if he had dug it at head height, he wouldn't have had to bend down.

Qing's lips stick out sharply.