\chapter{A Cunning Mind, a Wicked Heart (4)}

No, but what kind of butt kicking do I do with my heavy lifting?

Qing muttered, rubbing her numb buttocks to relieve the remaining tension.

"No, I feel like I'm falling into some kind of trap."

It was a hole made to show the setting sun, so wouldn't it be a natural instinct for people to look into it without realizing it?

Judging by this old man's personality, this was definitely intentional.

If there was a later person who figured out whether it was my imagination or a descent, I would have intentionally placed the hole in an ambiguous location so that I could kick his butt.

"Tsk. Okay."

The Great Emperor Mucheon or the Great Emperor MuQing clicks his tongue and makes a foul noise towards Qing.

"What kind of mother were you, imitating someone who doesn't have the right destiny? Do you think raising a child was easy?"

"You've never raised a senior citizen. You've never raised a child, let alone a student. Everyone says raising a child was difficult."

"Yeah, you said it well. It's hard enough to even support myself, what kind of child am I raising? There were so many people who devote their lives to training and end up old and dying without ever seeing a single sight. You're so incredibly relaxed."

The life of the Great Emperor Mucheon was nothing but training, and even though he reached a lofty realm of unknown heights, he always looked upward.

Lovers, children, and students were nothing more than mere passing glances, and the sole purpose of life was to study.

"No, I don't want to live a life so obsessively focused on training. Besides, I don't necessarily have to learn martial arts to use them, and I don't want to just rush ahead, aiming for the next level."

"Huh. What could be more important than self-fulfillment? And what's the use of it? Who do you think it's thanks to that you sect members were living so well?"

"Hmm."

Come to think of it, you've beaten up all the bad guys, smashed everything, and completely turned the martial arts world upside down.

Now that I think about it, isn't it reasonable to have doubts, and to take preemptive measures before they become a hindrance to your practice?

The Great Emperor Mucheon smiled brightly at him.

This was because the inner mental entity, Hosooin, who claimed to be the illusion created by Qing's mind, also known as the Great Emperor of MuQing, could read Qing's inner thoughts.

It's bound to be confusing.

No matter how high the level of the Great Emperor of Mucheon is, it would be difficult for him to read people's minds, so I think the image I created after seeing the traces of the Jeolgeombyeok was correct.

That being said, there were also some rare moments where it seems like it's real.

"That's the path the elder took. I have no intention of spending my life practicing and then dying or ascending to heaven. What kind of perfection was that? Just being able to protect my friends and family was enough for me."

"Well, was that really true?"

"What do you mean, was that really true?"

"You probably don't know, since you're still struggling in the humble realm of Hwagyeong. You seem to be able to even begin at the bare minimum. Well, let's see if you can surpass me and still say something like that."

Look at it now.

Is this what the Great Emperor of Wuqing in my imagination would say?

"What can't you do? Honestly, you already know that. Isn't your current state of flying on two legs and smashing rocks incredibly enjoyable? Do you truly believe that the path you're pursuing, the unlearned skills you're using to protect what you own, was truly worthy of your calling?"

"Wow. Do you know you look like a demon right now? Are you perhaps a Thousand-Year-Old Saint wearing human skin?"

"Huh. Your state was like that. If you could love yourself, you wouldn't beg for it from others. If you don't have it yourself, then you have to ask for it from others, right?"

Qing's eyebrows twitched.

"Can you stop this unwanted psychological counseling? Hurry up and show the Movement."

"Hmph. You have nothing to say, so you'll just change the subject. Hey. How can you become a great person and become a grand duke with such a weak heart?"

And yet, it was the Great Emperor Mucheon who reached out and grabbed the sword that was swirling and forming a shape in the air.

"Inseok, don't you feel anything after seeing the martial arts of the Kongtong guys?"

"Not really? All I saw was how to handle the Qi Gate. Oh, maybe I should have looked at the Bokma Sword first?"

"If you've seen the secret, you've seen it all. Our shared history was truly a practice of military service. It wasn't about martial arts as a form of learning, but about being true to the purpose of harming others and taking their lives."

In the past, the common people built a Taoist temple and established the Kongtong school by adding Buddhist meditation and Confucian examples based on Taoist thought.

But the root still belongs to the murderers.

Because the very act of killing that harms the opponent was considered the essence of nothingness.

So, the common ignorance may seem vain on the outside, like a monk who has embarked on a Mahayana journey, but deep down, it harbors a strong murderous intent.

The whole thing was the Bokma Sword.

A sword that holds a demon in its stomach.

Emperor Mucheon nods.

"That's true. No matter how much it's a path to perfection, a practice of cultivating the Tao, isn't martial arts ultimately a technique for harming your opponent? A cunning mind, a vicious heart. That's why they say if you're not vicious, you're not a warrior."

"Huh."

Qing blinked.

The evaluation of the Great Emperor Mucheon has always been skewed.

I don't like this and I don't like that, so why bother to leave a comment after seeing the old school's martial arts?

'You were wrong and I am right. Do this.'

It was a scolding, a training, a reprimand.

Why was it all just praise?

Then, the Great Emperor Mucheon laughed fiercely.

"There were those you like, and those you don't. While acknowledging the fundamentals of martial arts, isn't the spirit of perfecting them through the principles of martial arts the very essence of the Bokmageom?"

And then followed.

"It's just frustrating that they're just lacking in skill and haven't been able to produce any real experts yet."

As expected, it was an old man who was going well but then got twisted.

"Okay, enough talk about the losers. Watch this, you smart bitch."

The Great Emperor Mucheon straightens his sword.

A rare pose in Zhongyuan, with the blade standing straight between the eyebrows, slicing the face in half.

Because it's a really sloppy posture that's just a little cool without any benefit, and to put it bluntly, it's just a superficial, idiotic posture.

If you put a sword in front of your face, you're blocking your own vision, and even if an enemy attack comes flying at you, there's no way to extend it, and even if you try to block it, your head will be split by the blade.

However, Qingdo was now quite knowledgeable about the person known as Emperor Mucheon.

Anyway, if you were a master like Mucheon Daeje, you just need to look cool.

Rather, it would be better to expose the enemy's weakness and induce an attack.

As if Qing's thoughts were correct, the Emperor Mucheon smiled as if he was amazed, and then pulled out the sword and slowly lifted it.

It was a slow movement, like taking a jockey's saddle.

However, at that moment, a single ray of starlight, created by humans, shot out, and the strong energy that had passed before Qing's eyes touched the cliff and naturally dug into it without a sound.

He also draws his sword as if possessed.

The first meal was the only meal for infants.

It was a declaration that Buddha, as soon as he was born, cried out instead of crying, saying, "I alone am the most precious one in the whole world, above the heavens and under the heavens."

That was why, when the one who was the only one has the will to sway the world, he swings his sword and the world approaches.

This was the ideal of becoming heaven itself.

The three herbs were a kind of herb.

Only by setting foot on the earth can one unleash all of one's power, and only then can the power of man reach the heavens.

It was only when you know your place that you can reach the sky.

Because I am soon to be the center of the world, because I am soon to be like the earth itself.

And between the first and third seconds.

Between the sky and the earth.

A point that does not touch either the sky or the earth.

The point between heaven and earth was human being.

Qing sword pierces the point.

A human sword that pierces humans.

By nature, following naturally without any preparation or expression.

Because it was as natural for people to harm others as breathing and blinking.

\textbf{Solitary Nine Swords, Second Movement.}

\textbf{無毒不丈夫. Wudu Bu Zhangfu. No Poison, No Man.}

If you're not ruthless, you're not a hero.

In that moment, Qing realized that he had fully understood the introduction to the most far-reaching martial arts left behind by the highest-rising warrior.

The first three Movements of Solitary Nine Swords were the attitude toward life left behind by the Great Emperor Mucheon.

A downward slash that slice the world apart.

A secret stab that harbors human malice.

A tower that stretches toward the sky, relying on the earth.

Hold yourself up against the heaven.

Don't forget that you were only human.

Stand on the ground and look up to a high place.

But um.

Qing looked at Mucheon Daeje and said.

"Hmm. No Poison, No Man. The name is a bit strange."

No Poison, No Man.

It was a phrase from Ma Zhiyuan's work Autumn in Han Palace\footnote{漢宮秋; Han Gong Qiu}, which means that if you're not ruthless, then you're not a man.

For reference, in Zhongyuan, if a woman was ruthless, she was not treated as a hero, but simply as a wicked woman.

Although Cao Cao was treated as a traitor, his cruelty in burying people alive was evaluated as a necessary act in the times of chaos. Meanwhile Empress Dowager Lü, who brutally executed Lady Qi, who was causing chaos in the country due to her relatives' tyranny, was treated as the world's most wicked woman.

Well, it doesn't quite fit.

"Why isn't there also a term 'woman Zhangfu'?"\footnote{A pun. 婦 (Fu) meant married woman. But while 丈夫 (Zhangfu) is a valid word, 丈婦 doesn't exist}

"No, I'm completely alone."

There was only me in Dokgogugeom.

From the very beginning, the name of the martial arts was given to someone who was searching for a sword alone. Isn't it an ambition to dedicate everything to the pursuit of a perfect sword, a complete sword?

"Huh. So, you're saying you practice martial arts alone or in groups? Just look at your friends. Even if you're at the peak, you could somehow manage to reach Hwagyeong with some kind of spirit. Do you think those guys will ultimately be of any help to you? You're the type of girl who'd train alone, but you're just spreading the word that you have friends, and now you're even playing house, taking care of the kids. So, aren't you just a burden?"

"A burden, that's harsh……."

That's why Dokgo Gugeom and I don't get along.

If you say that you don't need anything else and that you should only be crazy about martial arts, then of course, if you say that the martial arts called Dokgo Gugeom was the most crazy martial arts that was not worth going crazy about, then that's not true.

"Fate is futile. Only your own accomplishments will make you whole. You'll realize this when you reach a higher level, so there's no need to nag you further."

"You know that if you come out like that, it'll only make people feel more repulsed, right?"

"Huh. Don't regret it later, thinking you could have saved a few more years."

And then, poof, the Great Emperor Mucheon suddenly disappeared.

Hmm. Are you crazy?

Since he was an old man who reads my mind and does whatever he wants, he may have been hurt because Dokgo Gugeom and I didn't get along.

When Qing came to her senses, she saw Yi-mei in an awkward position trying to catch her.

"Hmm? What are you doing?"

"You won't collapse? They said you usually collapsed after seeing Absolute Sword Wall?"

And then Qing, oh.