\chapter{Journey to Shaolin (7)}

And then, Seol Riri turned around again.

"Where are you going now?"

"Fruits……"

Knowing that what she was saying was absurd, her voice lacked
conviction and trailed off.

"Can you even tell which ones are edible and which ones aren't? Isn't
that place, Binggung, just full of ice?"

"I can distinguish apples."

"I just can't with you. Do you think apples grow on trees in the
backyard? And it's almost July, why are you looking for apples?"

Qing was an expert in foraging for food in the mountains.

It should be clarified that she was not an expert in survival but rather in
scavenging.

Due to her Constitution, she was an expert in eating just about
anything. However, she was utterly ignorant about the toxicity or safe
consumption methods of ingredients.

Still, she had a rough idea of what tasted good and what didn't. And
usually, for most people, something that tasted 'bad' was synonymous
with something that would kill them if they ate it.

"So, what fruits are in season?"

"At this time of year, hmm. Peaches? Although they might still be a bit
unripe."

"Peaches."

Seol Riri swallowed hard, and a faint smile appeared on her
expressionless face.

It seemed she liked peaches.

And then, she tried to turn around again.

Qing, dumbfounded, grabbed her once more.

"Hey, do you think peaches are just hanging around in the backyard?
Delicious fruits don't just grow wild like that."

"No. I saw them on the way here."

"Those are wild, unripe peaches. They're sour, bitter, and can upset
your stomach."

Seol Riri carefully examined Qing's expression. It seemed she was
trying to figure out if she was being lied to or not, unable to fully trust
her words.

"Sigh, this is going to be a disaster if I let you go. Fine, let's just go eat
dinner together. How can you just wander around without any money?
Do you have no sense of caution or prudence? Especially as a woman.
What are you going to do for food, and where will you sleep? On the
streets?"

Qing (the wild vagrant) clicked her tongue and spoke.

Seol Riri's gaze turned sharp, as if she had been poked where it hurt.

"Why? Do you have something to say?"

"Yes."

"Oh, really? Then go ahead."

"I don't want to."

What was she even trying to accomplish?

At least, it was clear she had no friends.

Even that prickly hedgehog, Miss Moyong, who seemed to have a
thousand times more inferiority complex than she had the right to, had
a group of followers, whether they were called the 'Fellowship of True
Friendship' or the 'Fellowship of No Men'.

"So, are you not going to eat with me?"

"No."

"You're going to eat, right?"

"Yes."

A mischievous smile appeared on Qing's face.

Then, all you have to say is 'I'm hungry, please buy me some food', she
thought, but then she decided it was too petty to hold food hostage like
that.

After all, one should never be petty about food. It was too much.

"Let's go. Let's have a feast today."

Which restaurant served the best Buddha Jumping Over The Wall?

It was actually a very difficult question.

Because Buddha Jumping Over The Wall wasn't like some tonic food that one
would just grab whenever they felt like it. It was a dish that even in the
Zhongyuan, was considered one of the most luxurious dishes,
perhaps only eaten once a year on very special occasions.

So if you asked people on the streets, they would only know the places
they had personally tried. And if you asked the waiters, they would
always say their restaurant was the best, so that wasn't reliable either.

However, when one had a burning desire for food, the mind worked
wonders.

"Hey, waiter. How much is your Buddha Jumping Over The Wall?"

"Ah, Young Lady! We serve it starting from fifteen taels. If you'd like to
be seated in the Beggars' Section, it starts from five taels……"

"Hmm. We'll look around."

The term 'Beggars' Section' was used because it was the most visible
seat in the establishment.

If two beauties were seated there, business would surely boom.

As such, Qing dismissed them.

"We have it starting from twenty taels……"

"If you'd like to be seated in the Beggars' Section, we'd actually have to
serve you instead……"

"Our basic starts at twenty-five taels."

Then, Qing finally found the answer.

"Well, this place has some expensive items."

"Sounds good. Are there any cool seats available?"

"Oh my, of course!"

Thus, Qing settled with Seol Riri at a spacious corner table on the top
floor of the restaurant.

"So, which Buddha Jumping Over The Wall would you like to have? We have
regular Buddha Jumping Over The Wall, Premium Buddha Jumping Over The Wall, Supreme
Buddha Jumping Over The Wall, One-and-Only Super Supreme Buddha Jumping Over The Wall, 
and the Ultimate Super Supreme Special Edition Buddha Jumping Over The Wall."

It felt like she should just pick one already.

Qing suppressed the urge to succumb to such a feeling and ordered
the Ultimate Super Supreme Special Edition Buddha Jumping Over The Wall, along
with some fried eggplant and a few vegetable dishes for a balanced
diet.

The waiter, having caught a big fish, shouted the order at the top of his
lungs, with a voice that rivaled a lion's roar. Then, he scurried away.

And so, as they waited excitedly for the food…

"……"

"Miss Seol? Isn't the weather quite hot these days?"

"Yes."

"……"

"……"

She didn't initiate conversation, and when an attempt was made to start
one, she cut it off with curt responses, making her a truly difficult
person to be around.

After some awkward time spent together in such a manner, the long
wait finally came to an end. A luxurious pot was placed before them and
as the waiter lifted the lid, the sweet scent unique to Shaoxing wine
spread, along with all sorts of delicious smells!

"Whoa. That smells delicious already. Hm? Miss Seol? You're drooling."

"I'm not."

Seol Riri wiped the corners of her mouth with her sleeve.

Even if that wasn't the case, her gaze was already fixed on the pot.

When asked what was in Buddha Jumping Over The Wall, one could simply say it
was a stew made with all kinds of delicious ingredients.

Among them, there were a few essential ingredients such as shark in,
sea cucumber, abalone, and the best dried meat of Zhongyuan
called Hwatoe.

Of course, since they were inland, the shark fin was omitted, and the
dried sea cucumber was a bit shriveled, but just looking at all the
ingredients made one smile naturally.

Thus, Qing first served Seol Riri a generous bowl and then filled her
own, finally starting their late dinner.

Qing was always someone who ate well.

Because the expression 'gobble up' suited her better than any other
woman in the world. It was hard to say that she ate, even with the most
positive of spins.

But Seol Riri also ate well.

At first, she looked at the unfamiliar dish with suspicious eyes, poking
and prodding at the ingredients before finally putting a piece of sliced
duck egg into her mouth-

Woah. What's with that smile?

Qing stared blankly at the blossoming smile on Seol Riri's face.

Her face, which was already to her liking, was adorned with a bewitching
smile that bloomed with a blush, making even Qing forget to use her
chopsticks.

Of course, her body remembered, so her left hand (since her right hand
was completely wrecked) automatically moved to stuff her mouth,
surprising her tongue and jaw into working, chewing, and eating
properly.

"Haeut, hat, heuaaa."

People from the North Sea region tended to eat everything piping hot.

This meant that they could eat hot food very well.

Even as she abandoned all decorum and started to inhale the food,
Seol Riri had a different feeling from Qing's style of gobbling. How
should she put it? It was, uh… Why are you eating so… seductively?

Suddenly, the customers dining on the same floor turned their heads at
the sound of a woman's moan.

And then, the customers were either struck by a calamity or were
blessed with a sight unlike any other in the human world.

Two beautiful women were having a meal, and one was stuffing food
into her mouth as if her cheeks would burst, chewing ferociously like
she was devouring her parents' enemy.

It was a scene that would make anyone say, 'What a disgusting lack of
table manners. Not even a pig would eat like that'. However, due to her
beauty, it felt like a strange and peculiar experience, as if there was
something appealing about it.

And as for the other woman, she ate her food in a way that could only
be described as adorable, but with every breath, she let out an
affectionate moan.

Though it had nothing to do with this, the customers suddenly crossed
or demurely folded their legs. It was truly a curious thing.

Regardless, Seol Riri had already lost more than half of her mind.

The Binggung was not well-off.

The people of barren lands were originally poor. This was because
pantries were scarce. After all, pantries were only made after people's
stomachs were filled.

Thus, when Seol Riri was ordered to capture the criminal and set out
south, she did not receive a large sum for her expenses from the start.

It was partly due to their circumstances, but also because they thought
she would quickly apprehend her target.

After all, wouldn't a Binggung person stand out in Zhongyuan?

And wouldn't it be easy to track them down by asking around?

The people of Binggung did not think that Zhongyuan was such
a vast land that was so large it was almost infinite.

They thought their own icy plains were the largest land that reached the
ends of the earth.

So, while staying at the Wulin Alliance, Seol Riri had been eating the
food of the Wulin Alliance.

Occasionally, when she felt like eating something tasty, she would go
out to the Dragon and Phoenix Assembly and eat the banquet dishes.

For reference, Peng Daesan's evaluation of the banquet dishes was that
they were made with the assumption that they would be cold, thus
being visually pleasing but lacking in taste.

However, even that was delicious to Seol Riri, making her think that the
people of Zhongyuan were being deceitful, enjoying such things
only for themselves. But is there any warm, hoooot food?

This was why Seol Riri often showed her face at the Dragon and
Phoenix Assembly, despite having no friends.

Moreover, since she completely blocked any approach from others, she
had never been treated to a meal by anyone else.

Therefore, this was the moment when Seol Riri encountered a proper
Supreme Delicacy for the first time since her arrival at Jianghu, and it
was also a dish that perfectly suited the tastes of a North Sea native,
who would say that anything not boiling like lava was cold.

Thus, the two women's combative meal continued, and on the top floor,
which had the most luxurious seating in the restaurant, the turnover of
tables completely stopped as the other customers could not breathe
properly and were too busy spectating.

"Hooah. I'm full."

Leaning back, Qing patted her swollen belly. It was almost as if she was
five or six months pregnant. In fact, she was actually raising something
inside, surprisingly a cute-looking Gu.

Seol Riri looked at Qing's full belly with a gaze full of wonder, before
lowering her head.

"Thank you for the meal."

It was an unexpectedly polite gesture.

Is it because of the food? Did her favorability increase because we ate
together? Qing smiled and attempted to start a post-meal conversation.

"How was it? Did it suit your taste?"

"Yes."

Looks like that wasn't it.

"Since we've finished eating, shouldn't Young Lady Seol stop following
me and return to the Alliance?"

"I don't want to."

She didn't deny that she was following her, so it seemed she had no
intention of hiding it from the start.

"You said you didn't have any money. Where are you going to sleep
tonight? On the streets?"

Seol Riri, with a sullen expression, quietly stared at Qing for a long
time before casually throwing out a statement.

"I'll go back and sleep, so wait for me."

"Ah. You're going to go back now and sleep, then come back? Well, if
you leave now, you'll get there by night, and if you leave tomorrow
morning after breakfast, you can be back before lunch."

"Yes."

"Assuming that, what about tomorrow? I'm going to Mount Zhongnan,
so are you going to keep going back and forth to sleep every day?"

Seol Riri bit her lip.

"I'll sleep outside."

"Have you ever slept outdoors before?"

"Yes. Many times."

Seol Riri was simply ignorant of the ways of Zhongyuan.

She was, after all, a strong North Sea native who had forcibly taken root
in a land where people could not originally live.

"Don't be like that. Since it's getting late and dark, why don't we just
find an inn and spend the night before you head back?"

"I don't want to."

"I'm planning to make a big loop all the way to Sichuan. Are you
planning to sleep outside and follow me the entire time?"

"Yes."

She was also quite stubborn.

Qing just gave up on persuading her.

Well, if she follows me around, she'll get tired of it on her own and
leave, right?

"Alright. If that's what Young Lady Seol wants."

As Qing said that and was about to get up, thinking they should find an
inn…

"Where does Young Lady Ximen plan to stay?"

"I'm going to look for a place now."

"Then, when are you leaving tomorrow?"

Why is she asking? She's definitely asking because she intends to
keep following me.

Is it normal to ask this so blatantly?

Feeling a bit of mischief, Qing replied.

"Whatever I feel like. I can't sleep alone, you see? If I can't sleep, I
might just take off in the middle of the night. So, keep a close watch. In
case you lose me."

It was not just mischief, but also a warning to keep her guard up since
she said she would sleep outside.

Young Lady Seol is a Master in her own right. Uh, is calling a Peak
Realm nobody a Master an insult to Masters? A wanderer, then.

Young Lady Seol is a wanderer, so she should be able to take care of
herself as long as she's alert.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Being very wealthy, Qing booked a luxurious room in a high-class inn,
took a refreshing bath, and threw herself onto the high-class bed.

As expected of something that costs money, her body was completely
engulfed, making her feel incredibly comfortable.

If I stay like this, I'll fall asleep in no time. Hm. Sleep. Sleep.
However, sleep did not come.

To be precise, her body was tired, and her mind was exhausted, making
her drowsy. But when she closed her eyes and laid down, she couldn't
fall asleep because she felt uncomfortable all over.

She felt like she had dozed off a few times, but each time, she woke up
with a very unpleasant feeling, only realizing that the same nightmare
had been repeating itself every time she fell asleep.

Eventually, Qing ruffled her hair and sat up.

The bedroom was silent.

Fortunately, the sound of rain pouring down outside the oil-papered
windows made it not completely silent.

Qing had always liked the sound of rain, ever since she was back in her
hometown before her regression. Especially when she was comfortable
and at ease, the sound of rain was so very relaxing, calming the mind
and body.

Qing even opened the window.

Whooosh!

The refreshing sound of rain, almost like frying something, filled the
room.

Wow, the sound of rain. It's so nice. I want to eat pajeon.

Maybe because of that, her mind seemed to calm down as she listened
to the soothing sound of rain.

Now, if I lie down, I think I can sleep. This was a kind of premonition,
or rather, a conviction, that she would be able to fall asleep.

Thus, Qing quickly laid down on the bed to catch the wave of sleepiness
that had come after so long.

And so, whoooosh, such a refreshing sound of rain. As if all worries
were being washed away, it truly felt good and, I'm falling asleep, I'm
falli……

It was at that moment, just as she was about to fall asleep.

A sudden thought flashed through her mind. Her eyes snapped open,
and she abruptly sat up.

Ah, that's right! Young Lady Seol! 