\chapter{Journey to Shaolin (8)}

It was supposed to rain in July, but who could have imagined this? I must have been out of my mind.

But then again, Qing was always out of her mind, except when she was killing people or eating. So, no matter how much she reflected, the same thing would likely happen again in the future.

Still, Qing had some reason to feel aggrieved.

The life of a wanderer in Jianghu. She now had a small hut to return to in the Divine Maiden Sect, but she was still essentially drifting without a home.

The land of Zhongyuan was vast, and not only was it vast, but the altitude varied greatly from place to place. Some areas were by rivers, some were deserts, and some were coasts. 

As such, the climate also varied greatly, so she had no sense of whether it would rain or be hot at this time of year.

She hurriedly left the room, and near the entrance, a dozing boy jumped up.

He was one of those boys who would appear out of nowhere when it rained, selling straw rain hats beside the inn's entrance.

In truth, they were the sons or daughters of the inn's employees, taking advantage of the inclement weather to make some extra money.

Even the high-end inns had umbrellas ready, so it seemed like only she hadn't known it would rain.

"Hey. Give me two banggats (rain hats)."

"Ah. Fairy! Here you go!"

Startled awake by Qing's beauty, the boy handed over a large basket-like object without even asking for money.

"How much?"

"Ah! Right! One is a silver nyang."

"This? Is it woven that well?"

The boy shrank back.

"Two for one silver nyang……"

It was a miracle that the price suddenly halved, but it was still a generous price.

"You know my room, right? Bring me a bunch of dry towels."

"The errand fee is……"

"I'm buying two rain hats that are worth ten copper coins each at five times the price, you know?"

"Yes……"

Surprisingly, the boy knew the exact market price, so he couldn't haggle further and retreated.

Of course, even if he was a child, he was still a merchant of Zhongyuan, so he was tough. However, after being enchanted by Qing's beauty, his merchant spirit had not been able to 
exert its full potential.

Thus, wearing two banggats stacked on top of each other, Qing stepped out into the rain, the sound of the raindrops drumming on the hats echoing loudly.

A banggat was, simply put, a super-sized gat. Worn on the head, it extended far forward and covered the back down to below the buttocks, curving outwards to deflect rainwater.

The downside was that it was heavy, became even heavier when wet, and the rainwater that flowed off the back poured down like a waterfall, soaking the ankles.

But Qing's incredibly strong neck bones could easily bear that weight.

So, she stepped outside. And thought, 'Um. Right. It's pitch black……'

Heavy rain was usually accompanied by thick rain clouds, and there was no electricity in the uncivilized Zhongyuan at night.

The greatest invention in human history, which involved boiling water to turn water wheels, had not yet appeared.

For now, Qing took to the streets.

Her vision, which also transcended human limitations, gradually made out the outlines in the darkness.

Where could Young Lady Seol be?

She said she had slept outdoors a lot, didn't she?

Qing, as an expert in sleeping rough, hurriedly searched the places she had noticed while looking for restaurants.

But she wasn't there.

And then, a sudden thought struck her.

Did she sleep rough so carelessly that her knowledge is also careless? Did she crawl under a bridge to avoid the rain?

Water could rise faster than expected, and a rapid current was a far more formidable disaster than one might think.

So, Qing ran along the tributaries of the Han River, checking under the bridges.

But she wasn't there either.

Now, if she's not in a spot that seems like a good place to sleep nor under a bridge, then where in the world is she sleeping rough?

Or did she just go home because of the rain?

Come to think of it, Young Lady Seol was certainly capable of doing just that.

But if you're going home, you should at least say something. Why did you just leave without saying anything, making a person worry?

I just ran around all night in vain.

Still, it would be better if she had gone home.

But since she couldn't be sure, she couldn't just go inside.

After about half an hour of searching for Seol Yiri, Qing finally caught sight of her.

Talk about being in the dark right under the lamp's nose; she was squatting under a makeshift awning set up by a street vendor in front of the inn Qing had booked.

In fact, since Qing had jokingly mentioned that she might run away in the middle of the night, Seol Yiri had taken up a spot where she could watch the entrance.

Even with Qing's superhuman computational abilities, she had no idea, so she ended up running around in the rain all night for nothing.

But her physique was like steel, and she had already reached a realm where she was impervious to the cold.

If one had a good body, they wouldn't suffer too much even if their head was a bit lacking.

"Hey, Young Lady Seol. Have you just been standing in the rain? Why are you so stubbornly getting rained on? Aren't you cold?"

"The Far North fish are much colder."

Indeed, for the people of the Far North who lived on a frozen lake all year round, summer and winter were just a flow of cold days and colder days.

"It'sh shtill hot in the Far North at thish time of year."

"Your voice is already trembling, you know."

"Nooo, I'm not."

In truth, if one were to ask whether it was cold or not, the answer would be that it was not cold at all.

Rather, it was perfectly refreshing.

It was the kind of weather where one might feel a liberating coolness, like in a movie where someone throws their umbrella high in the air and laughs under the pouring rain.

But it was about standing for a long time while being continuously hit by raindrops that were so thick they felt like they were striking the body.

This was a completely different matter from whether it was cold or not.

The human body was made to regulate its temperature through the air, so when the wet body was constantly hit by new raindrops, it could only helplessly keep losing its warmth.

"Sheesh. You said you've slept outdoors a lot? Do people sleep in the rain in the Far North? You're going to end up a corpse like this."

"It doeshn't rain in the Far North."

"It snows, doesn't it? Do people sleep in the snow there?"

"No."

"Then why would you just stand there and get rained on when you know it's not snow?"

"It'sh rain, not shnow."

She never lost an argument.

Qing clicked her tongue, and Seol Yiri, despite saying all that, quietly followed her and stood up. It seemed like she, too, thought this wasn't quite right.

When they returned to the room, sure enough, her complexion, which was originally pale enough to be considered sickly, had turned a shade between purple and blue, losing its color and turning dark.

Fortunately, the boy selling umbrellas had brought plenty of dry towels, so Qing first wiped her face roughly, wrung out her hair, and after struggling with her wet clothes that clung tightly to her body, she finally managed to wipe off the moisture with the dry towels.

Then, she laid her on the bed and covered her with a blanket, making her think that this was what it felt like to take care of a child, making her anew appreciate the great grace of her parents who taught her to be true and upright……

"Hey, why would you sleep rough in the rain?"

"I don't shleep."

After being tucked into bed with all the moisture wiped off, Seol Yiri's speech had returned.

"Then you'll die. Cold and rain are completely different. You said you've slept rough a lot, didn't you?"

"It doeshn't rain in the Far North."

"It snows, doesn't it? Do you sleep rough in the snow?"

"No."

"No? Then why were you just letting yourself get rained on?"

"Becaushe it'sh not shnow."

She never lost an argument.

Qing clicked her tongue and finally began to dry her own soaked body.

She had worn a banggat, but the rain was so heavy, and she had been running around so much (uselessly) that only her head, shoulders, and back were mostly dry.

Seol Yiri's gaze landed on Qing's figure, then on the towel wiping her body, and finally, it reached the arms that had swollen to twice their size and turned black, where it stopped as if nailed, staring endlessly.

Regardless, Qing was tired from the night's ruckus (though her body was perfectly fine), and the sense of relief made her feel like she would fall asleep soon.

After roughly wringing the moisture out of her clothes, Qing slipped under the covers.

Then, Seol Yiri spoke.

"Hey."

"What?"

"I can't shleep if shomeone's there."

"Then don't sleep. You couldn't sleep even when you were standing in the rain outside anyway. Isn't it better to not sleep on a warm and comfortable bed without getting rained on?"

"……"

Seol Yiri seemed to pout as if she was upset, pressing her lips together tightly.

"So, whether you sleep or not, do as you please. I need to sleep."

"……"

Is she perhaps a bit too proud?

Since there was no response, Qing thought she was just being her usual self. But… Why is her breathing so heavy?

"Young Lady Seol?"

"……Dorong."

Qing frowned deeply.

What? She can't sleep if someone's there?

She fell asleep as soon as she said that bullshit.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

'If you're curious, you should ask,' is a saying that holds true.

And as expected, Seol Yiri caught a cold.

"Seriously, why would a martial artist catch a cold."

"I'm not."

"Your nose is completely blocked. You're sniffling right now."

Seol Yiri wiped her nose with the blanket.

"It'sh not shniffles."

"You're really making this hard……"

Martial artists could catch a cold.

It was very difficult, but it happened.

For example, if one were to stand in heavy rain without circulating their Inner Qi to protect their body, it wouldn't be much different from an ordinary person with a strong body getting rained on.

So, Seol Yiri caught a cold.

A very severe one at that.

"Didn't you circulate your Inner Qi while it was raining?"

"It wash hot."

In other words, she heard that during the ten or so days of summer in the Ice Palace, the sun shone brightly. On such days, everyone would come out and enjoy the sunlight, saying it was a refreshing day.

And even the coldest days in Zhongyuan were much warmer than that.

Now, the sultry heat of late June felt like being in a hellish inferno to Seol Yiri.

So, she had been diligently circulating her Ice Arts to keep herself cool. By the time the heat had subsided at night, her dantian was empty, so she would circulate her Qi to recover. Then, during the day, she would keep her Ice Arts going.

"You used up all your Inner Qi to stay cool, so your dantian was empty at night?"

"Yesh. And shtop ushing that informal tone."

"Ha. Even with that runny nose, you still want to draw lines? Can you even pronounce it properly?"

Seol Yiri glared at Qing fiercely.

Qing responded to her.

"Why don't you try wiping your runny nose first before glaring? Honestly, it's really funny, but I'm holding back, you know?"

"Tch."

"Anyway, I'll buy you a hearty breakfast, so eat up and go back. No, I'll get you a room and pay for your meals until your cold is better, so rest well for a day."

Martial artists could catch a cold, but they recovered quickly.

A cold was nothing much; with a day of rest and circulating one's Qi, one would recover as if nothing had happened.

"I'm not going."

She was trying to pronounce it clearly, but a blocked nose was a blocked nose.

It was a pitiful attempt.

"What, you're so stubborn. Why are you even trying to follow me? It's going to keep raining since it's the rainy season, you know? You don't even have money or a change of clothes."

"Yeah."

She's so stubborn. Seriously.

Moreover, wasn't there a limit to being thoughtless?

It wasn't as if Qing would act like a mother and show endless mercy. She had no reason to take care of a woman who set boundaries, not wanting to be a companion.

If she was a bit more friendly, it would be different. She's pretty and cute, but that's about it.

Hmm? If she's pretty and cute, is it worth the effort to take care of her? It's usually called a pet or something, right?

Qing shook off the unnecessary thoughts.

Anyway, she's suffered once already, so she must know how scary the rain is now, right?

"Hmph. Then do as you please. I'm leaving, so you can live here, Young Lady Seol."

"Wait. That'sh being mean."

Seol Yiri didn't have a change of clothes.

Since it had been pouring since yesterday morning, there was no way her clothes would have dried in the meantime.

Seol Yiri, startled, tumbled out of bed and grabbed her still-damp underwear, hesitating. Meanwhile, Qing, an expert drifter, had already changed into spare clothes and finished preparing to leave.

"Are you coming or not? I'm going to eat something similar to pajeon since it's raining……"

There was a similar dish to Korean savory pancakes, called jeonbyeong.

One of Qing's hometown's dishes was a type of savory pancake made with buckwheat for the batter, stuffed with a kimchi filling, but in reality, the original jeonbyeong referred to a type of food made by thinly spreading wheat flour or similar dough on an iron griddle.

It was also a common breakfast that people of Zhongyuan liked to buy and eat on the go.

"Then, should I get a bottle of Hwangju too? As expected, when it's raining, you need to have some takju with your pajeon. Something sweet."

While Qing was pondering, there was a rustling sound of a door opening, followed by quick, seemingly hurried footsteps, and then an 'Ah,' a sound of relief with a stuffy nose.

This bitch is really following me.

She's like a leech. A leech, I tell you.

Qing sighed deeply and turned around-

Since they said it was hot in Zhongyuan, Seol Yiri's attire consisted of a single-layered robe that served as both a top and a skirt, and it was a thin, sky-blue type.

But her not-quite-dry clothes clung tightly to her body, revealing two distinctly protruding parts on her upper body.

Qing shouted in astonishment.

"Hey, what are you doing! Dressed like that……! Go back inside right now!?"