\chapter{Journey to Shaolin (4)}

The Empress clasped Qing's hand tightly.

It might have been because Qing's hands were always cold due to
Demonic Arts, but the warmth conveyed felt so hot it almost burned.

"To see you like this, restored to your former beauty… It truly feels like a
dream. Yes, you have met your mother, so do you not have anything to
say?"

"Uh, about that."

Qing rolled her eyes.

The Empress smiled benevolently.

"Yes. Speak freely. What is there to hesitate about between mother and
daughter?"

"Well then, can I put on some clothes now……"

"Oh my. What is there to be shy about in front of your mother? Well, I
suppose Shaoxia has become shy after losing her memories. Just as it was
before……"

"Shaoxia……?"

"Yes. Shaoxia. It is the name you have forgotten. This is how it is written in
characters. It might be your first time seeing these characters, though."

The Empress wrote on Qing's palm.

朱玿鶷. Zhu Shaoxia.

It was a character so complex that it had many strokes.

Shaoxia, a beautiful bird sculpted from jade, as white as snow, meant
'egret'.

The grace of the imperial family emerged in their names. Commoners
could not dare to use the same names, as the names of the imperial
family were so common that one could unknowingly become a traitor
without even realizing it.

Therefore, the imperial family made it a point to use unique characters
that were rarely used by ordinary people, as a consideration for the
common folk.

"But still, shouldn't I put on some clothes……"

"Tsk tsk. Are you so ashamed and embarrassed by the body your mother
gave you? A large bosom represents the maternal love that will embrace
all under Heaven and large hips are a beneficial grace that allows for
multiple births. Yet, how could my Princess always try to hide and
conceal them?"

"No, it's not that."

Qing was not ashamed of her body.

Sometimes, when she looked in the mirror, she would marvel at the
ever-new and thrilling beauty it held.

If it was now, she could even understand that foreign god, Mr. Nar, who
was said to have burst his mother's insides because he spent twelve
months of the year staring at his own reflection in a stream.

So it wasn't that she was ashamed and wanted to hide, but rather that it
was awkward and embarrassing to be naked in front of a stranger.

Especially when the woman who suddenly appeared and claimed to be
her mother had the warmest gaze, as if she wanted to memorize every
single downy hair on her body, thus thoroughly scrutinizing her.

"Are you uncomfortable? Do you not feel any affection even with your
mother in front of you? This mother, what is blood, after all? Ever since
the day a fake that called herself you entered the palace, I knew
immediately that something was off."

The wicked women said they had fully healed her daughter and brought
her back. But because of some inexplicable intuition or transcendent
ability that only those of the same flesh and blood had, she looked
nothing like her daughter, constantly feeling awkward and strange.

Then, one day, a court lady attending to the princess said, 'It is truly
strange, but the two beauty marks under her chest have spread and
merged into one'.

At that moment, her mind flashed and everything became clear at once.

Ah, those wicked nuns have used some evil trick to put a monster in
my daughter's skin.

If she had only one child, she would have risked her life to fight the
wicked women, no matter what. But she couldn't bear the thought of
harm befalling her remaining children, so she suffered in silence.

Then, her long-departed daughter appeared in her dreams, making her
decide to offer a Buddhist prayer.

And when she could not bear the frustration of having no news, she
opened the window of her carriage and saw Qing's appearance,
causing her to jump out without realizing it.

At the same time, she felt no strength in her legs. As such, she knew not
the pain when she fell, despite disregarding the dignity of an Empress
and rushing out in a hurry. Instead, she hastened to chase after the
image of her daughter.

She knew from the ample bosom and hips that Qing tried to hide ever
since she was young, and from the slender line of her body that seemed
as if it would snap due to its frailness. But above all, she knew because
her daughter's face, the most beautiful face in the world before she
fell ill, was still there. Despite becoming even more beautiful, her
appearance from those days still remained.

Ah shit. Why am I even listening to this?

Qing's heart grew heavier as she listened.

Unintended body theft. Since the owner was already dead, it was more
akin to a trade-in? Or picking up something that was discarded?

Perhaps, she was just a grave robber.

The heart-wrenching story grew increasingly uncomfortable.

So, Qing tried to change the subject.

"Uh, by the way, am I of age? I've been lying because I don't know my
exact age."

"Of course. Since you were young, you grew so quickly that by the age
of ten, you were already taller than me. I thought you were growing fast
to show your mature figure before leaving, so I would tell you to live
long if you wanted to be a filial daughter to all under Heaven. How
could I have blamed you for wanting to go before your mother?"

The topic naturally returned to where it started, causing Qing to
swallow a groan and think of other things instead.

What? So when I first came here… Since it's been five years… I was
sixteen?

That was sixteen, huh… No wonder my chest seems to have gotten
bigger, I was still in my growing phase.

"Yes, after you left for the secular world, how did you live? They said
that once the Great Ritual was over, you would have no illness, and that
your latent talent would awaken, leading to the birth of the greatest
martial artist under heaven if you learned martial arts. Their words
were not entirely lies, seeing as your achievements have even
impressed that Eunuch. Still, it must have been a relief to be able to
protect yourself in the outside world."

"Um. I just got by. I lived well."

"Tch. How could you not tell everything to your mother?"

How could she possibly say that she was beaten by beggars almost
every day, that she survived on food waste, and if that wasn't enough,
she ate bugs, poisonous mushrooms, and leaves from the mountains
and fields? And when even that wasn't enough, she filled her stomach
with water, living the life of a beggar?

"Uh, at first, it was a bit tough, but I adapted quickly. Then, my Master,
ah, do you know Daoist Ximen Surin of the Divine Maiden Sect? She's
the strongest among women. Anyway, Master took me in, so I've been
eating well and living very well since then."

"Not only did Buddha protect you, but the Immortals also helped, huh?
This is truly a blessing. I must not only offer Buddhist prayers but also
hold an ancestral rite. No, I must hold that rite."

"Uh, you don't have to go that far……"

"No. What can a mother not do when her dead child has been returned
to her? Yes, and then, what else happened?"

"Uh, I made a lot of friends and traveled here and there. Ah, do you
know Mount Hua? Actually, the volcano there wasn't that kind of
volca……"

Qing chattered on, sharing stories of famous sights and attractions she
had seen in Zhongyuan.

She omitted all the stories about her hardships, so the Empress must
have thought she had a very comfortable journey, touring all under
Heaven.

Of course, that wasn't the case at all.

An ordinary young lady who knew nothing of the world must have gone
through so much, but the fact that she tried to hide it was even more
commendable.

"Yes. You said you could play the flute? Could you play a song for this
mother as well?"

"Ah. Yes."

Qing hesitated for a moment while holding Bokshinjuk.

Even the embarrassment of not being allowed to put on clothes
somehow subsided when she held Bokshinjuk.

But why can't I wear clothes?

Was there some strange custom in Zhongyuan where people
felt affectionate while looking at their child's naked body? Or was it
some kind of custom unique to the Imperial Family?

Of course, that wasn't the case.

However, the Empress's mind was stuck on her daughter's body, which
had been decaying due to a strange disease, so she was merely
examining her to see if there were any scars left anywhere.

As for what song to play, Qing hesitated for a moment before thinking,
'Parental Love'?

Hm. Come to think of it, I'm not sure if I actually remembered the
title.

Thus, Qing, while humming the lyrics under her breath, brought forth
the beautiful tones of Bokshinjuk, the sound that anyone would describe
as the sound of Heaven.

\begin{quote}
{\itshape The hardship of giving birth, you'd forget,
	
The struggles of raising me, day and night,

Teaching me to be true and right,

Dry spots for me when I wet the bed, you'd take the damp spots for
yourself,

Ooooh, how great is the love of my Tea……cher?}
\end{quote}

Qing continued playing.

After all, the performance had to go on.

\begin{quote}{\itshape Ooooh, I'll repay, my Teacher's grace}.\end{quote}

And then, she couldn't understand.

What? Why does it suddenly become about a Teacher in the chorus?

This wasn't right. It didn't feel right.

And why 'grateful'? 'Miss' is the right word here. Ah fuck, I don't
know. There's no way to confirm it either.

Embarrassed, even though there was no one in this world who could
understand, Qing quickly moved on to the next song.

Carousel by Mr. Jo, no, the one that would be born in Japan in the far
future, and some famous songs from her hometown that she couldn't
quite remember, were all connected.

"Oh my, to think you've grown so much. Of course, your body had long
since grown, but……"

The Empress shed tears again.

Ah shit. This is making me feel weak.

But still, what can't be done can't be done.

Qing steeled her wavering heart.

If it was a complete stranger, she could have pretended to be a fake
daughter.

Look at that old geezer with dementia over there, for example.

But with the Empress, she couldn't do that while wearing the skin left
behind by her dead daughter. At the very least, she shouldn't.

But her heart kept wavering.

Isn't he just like that old geezer?

But do I have the right to do this as a corpse thief?

In the end, she couldn't be cruel and kept playing along, thus wasting
time without end.

What saved Qing from such a dilemma was Qing herself.

To be precise, it was her empty stomach, which roared in protest
because it hadn't been fed even though it was past dinner time.

Grrrrrrrrrrrrrr!!! (Give me food now!!!)

"Oh my, my child must be hungry. What a terrible mother I am, not even
realizing my own daughter is starving. Oh."

And then, she shed tears again.

"No, it's not that. It's just that my stomach tends to be a bit loud. I'm
just a little hungry. That's all."

"No, that's not it. Now that we've been reunited thanks to the Heavens'
blessings, how could I, as a mother, not share a meal with my daughter?
It's just that I'm saddened by my own circumstances."

"Uh, can't we just eat together?"

The Empress smiled through her tears.

"No. The affairs of the Imperial Palace are not so simple. Having you
here for this long is already attracting attention. I was able to recognize
you as a mother, but if it were someone else, who knows what kind of
harm might come to you? So, we must part at this point."

"Ah. Yes……"

So, I'm finally free?

"Yes. My child. Do not worry. Just see, wear, and eat only the best
things in the world and wait in peace. This mother will restore what
you should have originally possessed."

The gaze of the Empress, who spoke as such, was truly that of the most
wicked witch under Heaven.

Qing was startled and hurriedly tried to dissuade the Empress.

"No, you don't have to do that. I have already decided to live as Ximen
Qing, a disciple of the Divine Maiden Sect-"

"That is not something to say. Bearing the blood of the Son of Heaven is
to uphold the Mandate of Heaven. If our child tries to avoid it, it will
only lead to greater sins. How can this mother bear to see that?"

"No, I'm really okay. I'm doing very well even now. So, please don't
trouble yourself-"

"My child. Let us embrace before we part. Come, let us embrace."

It's a lost cause. She's not listening at all.

I really hope she doesn't do anything unnecessary.

At the same time, there was a premonition that these words would not
be heard, as well as a foreboding sense that this would lead to
troublesome matters in the not-so-distant future.

But what could she do? Ah, whatever. I give up.

Qing gave up trying to persuade her and obediently leaned into her
embrace.