\chapter{Journey to Shaolin (6)}

Qing stood there, blinking her eyes repeatedly.

Huh? I'm not going to space this time? Um? Space? Why space?

Have I ever been to space? What's going on? It feels like something is
coming to mind, but…

But no, I shouldn't recall.

If I did, I would cross an irreversible fork in the road. That was the
premonition. No, a conviction that it was true.

But for some reason, she couldn't stop thinking about it.

It was as if someone was forcibly guiding her thoughts-

"Oho! Did you read the Insights! Indeed! The Ninth Movement! It's the Ninth Movement, isn't it?!"

"Ack."

Suddenly, a loud voice grabbed both her forearms, and Qing's thoughts were forcibly cut off.

"That's. Oof."

Qing's pretty face contorted.

It was the first time she had made such a face since she had possessed
this body, which was gifted with such a divinely beautiful appearance.

"Why, what's wrong!"

"Great Master of Martial Studies, my arm, my arm……!"

"Your arm? Why? It looks fine. More importantly, what about the
Insights? It's the Ninth Movement, isn't it?"

"Argh! M-My, arm!"

Qing's right arm began to spasm violently.

It was no wonder.

She had supported the weight of the entire world with one arm.

Even if it was within the Imagery, it was vividly remembered, and the effects remained.

From the rotator cuff of her shoulder, through the deltoid, biceps, and
triceps, to the brachialis, brachioradialis, and deep muscles below, all
the tendons of her fingers were overloaded at once.

In other words, she had a cramp from her shoulder to her fingertips all
at the same time.

"Oh my, what is this?"

After poking Qing's right arm, the Great Master of Martial Studies
quickly pressed on Qing's pressure points. It was to cut off the force
entirely from the arm and paralyze it.

"Argh! Argh!"

"No, what, why can't I find you pressure points? And why don't you
withdraw your Defensive Qi? I'm not trying to harm you."

"Agh, it's, automatic. I… Argh."

What was happening to Qing's Defensive Qi!?

Now that it had evolved into a Defensive Force along with her realm,
when the Great Master poked her with his fingers, the force that arose
fiercely from within was desperately defending against the Greatest
Under Heaven.

In truth, it was all useless since her already dead pressure points
wouldn't be found, and neither the Great Master nor the Defensive Qi
were doing anything productive.

"What? To think you've already trained your Defensive Qi to such a
level that it unfolds unconsciously? What kind of secret did Surin use!
Indeed, she did have a talent for raising disciples!"

Ah shit, it hurts so much!

While someone was spilling over in agony, with saliva drooling and
tears forming, another was just admiring her from the side.

No wonder her master used to call them bald monks!

It was the second time her shin had been kicked while trying to follow
the Celestial Martial Emperor, the third if including the first Absolute
Sword Wall encounter.

However, while witnessing Countless Changes, she was only at the Peak Realm, unable to properly see, feel, and experience, and was
nothing more than a bug compared to the Celestial Martial Emperor.

As such, the blow wasn't very big at all.

But now that she had reached the Transcendent Realm, she vaguely understood the Imagery and suffered a blowback.

Thus, Qing was drained of all her saliva and snot.

Fortunately, it didn't hurt to the point of tears, so that was a relief, wasn't it? Or perhaps not.

And then, Qing's pretty hand - which was, of course, the most evil and
beautiful in the world - was nowhere to be seen, swollen to twice its
size and looking like a pig's foot.

It looked as if the flesh had grown an inch in all directions.

It wasn't just her hand that was hidden in her sleeve; her entire right
arm, from the shoulder down, was probably in the same state. She
could immediately tell from the subtle pain that radiated throughout.

Seeing this, the Great Master asked.

"So, what is the rank of Shaolin? And, of course, it is the Ninth Movement, right?"

“Could you, maybe, pretend to care about my arm—urk. Glrk.”

Something suddenly shot into her mouth.

It smacked the roof of her mouth hard, then dropped deep into the back of her throat.

It’s a reflex—when something touches the back of your tongue, you swallow before you even know what happened. And so Qing did just that.

“It’s a Lesser Rejuvenation Pill. Just a leftover lump from crafting a Great Rejuvenation Pill. So? How do you feel?”

"I didn't mean to get an elixir, you know. And um, it wasn't the Ninth Movement……"

"It wasn't the Ninth Movement………"

The Great Master's shoulders slumped.

It seemed he was surprisingly concerned, even though he didn't seem to care much.

"It's the First Movement of the Solitary Nine Swords, a sword strike called Only I Am  Supreme."

At that, the Great Master pondered for a moment, then…

Slap! He struck his forehead with his palm in a lively manner.

In fact, this was a long-standing tradition of Shaolin, passed down from Great Master Huike, who was missing an arm.

"Indeed, the First Movement is better. Since all martial arts of the world originated from Shaolin, the First Movement must be the most fundamental. By the way, Only I Am Supreme. Can you interpret it?"

"Um. If I were to describe it as I saw it……"

Qing described what she had seen in the vision.

Then, the Great Master clapped his own forehead once more.

Slap!

"The cliff approaches you and gets cut by itself. Motion comes from stillness. Indeed. Indeed."

"Uh, isn't that nonsense? Can you just believe that?"

The Great Master smiled benevolently.

"When you swing your sword to cut your enemy, think of yourself not as a human, but as a sword. Does the sword move on its own to cut the enemy? No. From the sword's perspective, it feels as if the enemy is approaching and impaling itself on the sword."

If Qing had been from a science and engineering background, this conversation might have been very interesting to her.

In fact, there were those in Qing's hometown who claimed that an object moving and colliding was the same as an object stationary and being hit, thus they were indistinguishable.

If one were to classify them by their profession, they would be physicists, insurance adjusters, extortionists, and worm-like creatures in human form trying to tow vehicles.

"But I'm not a sword."

"Have you not already experienced the state of being one with the sword? A weapon is an extension of the body, so it is not wrong to say that it is the same as the body."

This was why martial arts were difficult.

Increasingly, it became entwined with philosophy, metaphysics, or some ideology, making it difficult to understand with just words alone.

It was precisely because it was something that could not be understood unless one realized it for themselves and established it firmly that it was called enlightenment.

"Um……"

"Moreover, it distinguishes between the self and selflessness. To erase myself from the world is selflessness, so if the world is erased, one exists alone."

The Great Master's expression was strange.

It was as if he wanted to sneeze, but couldn't, his nose tickling.

"Haiyaa. I'll have to try meditating to find out. I had a great desire to escort you, but I fear I must not miss this opportunity. This old monk must depart first."

"Then that's a shame. Please, go ahead."

"Thank you for understanding. Then."

And then, he suddenly leaped and flew, jumping more than ten meters
at once, kicking off the cliff, then kicking off the steep walls of the
gorge to the left and right, soaring higher and higher before
disappearing.

And then, Qing was left alone in front of the Absolute Sword Wall.

The medicine she had just taken, called the Small Revitalization Pill,
spread its cool energy throughout her body, while her swollen right arm
gradually increased in pain.

However, such things were not important.

In front of her were the great Insights left behind by the Celestial
Martial Emperor.

Qing realized the most important fact.

I'm hungry……

Krrrrrr!

Qing's stomach answered with a mighty roar.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Ximen Surin called the Shaolin monks bald monks.

Of course, it was already more like a martial arts sect than a temple,
though.

Moreover, what with the way the city of Dengfeng stretched all the
way to the front of Shaolin Temple at the foot of Mount Song, nestled
right at the base of the mountain.

As such, just beyond the wall of the temple were all sorts of teahouses,
restaurants, and high-end inns for pilgrims and tourists.

Of course, Ximen Surin didn't just call them bald monks for that reason;
it was simply because they were nasty bald bastards who wouldn't let
women in.

At any rate, this meant that Qing didn't have to embark on a long
journey of thirty thousand li to find a place to eat.

There was no need to worry about what to eat either.

Although Qing's intelligence could be considered low, it occasionally
excelled in certain areas.

Aside from the fact that her intelligence soared in front of enemies due
to the influence of Heavenly Slaughter, when it came to food, her brain
worked exceptionally well and she rarely forgot what she heard.

Thus, Budae-jjigae!

No, wait. Not that one.

Buddha Jumps Over the Wall!

Buddha Jumps Over the Wall meant that it was so delicious that even
Buddha would sneak over the wall to eat it.

Originally, it was a dish from Fuzhou, the capital of Fujian Province,
but it was sold near famous temples, and it was so expensive that not
everyone could eat it.

After all, it wasn't as if there was anything cheap about the ingredients;
all kinds of expensive, tasty ingredients were stuffed inside and then
drenched in Shaoxing wine, before being simmered. As such, it would
be strange if it wasn't delicious.

Thus, Qing wandered the streets of Dengfeng as a lone gourmet, trying
to figure out which restaurant did it best.

Since it was a top-tier dish where the ingredients determined the taste,
it couldn't be properly savored in mediocre restaurants.

While she was soothing her hunger with a meat bun from a street stall,
a rumor spread that a celestial maiden had appeared in Dengfeng.

As such, while walking around and receiving all sorts of attention, Qing
spotted an unexpected figure.

It was Seol Yee-ri, who had ditched her to eat meat alone, that
sneaky, conniving bitch.

She was also in a somewhat pitiful state.

She was standing on one side of the street, staring intently at
something. Following her gaze, it led to a street stall selling wonton
noodles.

What's going on? Why is she staring like that? Is it a really delicious
restaurant or something? Is it a famous eatery?

However, it didn't seem particularly busy; although he kept shouting
'Wonton noodles', no one seemed to be buying any.

Then what? Does she know the owner?

Qing was curious, so she asked.

"Miss Seol. What are you doing?"

"You."

"Why are you staring so hard? Do you know them? Or is it because it's a
delicious restaurant?"

Seol Yee-ri's lips twitched. She clenched and unclenched her fists,
hesitated for a long time, and finally gave an answer in a tiny voice.

"I have no money……"

Since the Ice Palace was not in a particularly prosperous situation, it
was basically a frozen neighborhood, making it a miracle for them to
even survive the cold. As such, there was no particular product coming
out from it.

When she stayed at the Wulin Alliance, they gave her lodging, food,
and sometimes even pocket money. But even if they hadn't, there
wasn't much use for money for a woman anyway.

She would occasionally use the pocket money that came out for
expenses that a woman naturally needed, but there was nothing left
after that.

In such a situation, she had chased after Qing without any plan to track
down criminals, only to realize the harsh reality of poverty.

Seol Yee-ri was a pauper.

Qing was dumbfounded.

"Wait, you were so confident when you said you were going to eat
meat, but you had no money? Wait, Miss Seol, where are you going?"

"Hunting."

Her words were still short, so it was unclear whether she intended to
hunt to get meat because she had no money or to earn money through
hunting to buy food.

However, one thing was absolutely clear.

"You're going to hunt on a mountain where a large temple is located?
Right in front of Shaolin's main gate?"

At that, Seol Yee-ri's body froze.

"Is that not allowed?"

"Of course, it's not allowed."

Seol Yee-ri's shoulders drooped slightly.

At that sight, Qing tilted her head.

What's with her? She's completely clueless, isn't she?

To be called clueless by Qing… If disciples of the Ice Palace or
Namgoong Shinjae, who knew her, heard this, they would say it was
better to bite their tongues and die.

Of course, if they really did bite their tongues, they wouldn't die from
it, so they would just say that she was a bitch who was worthy of being
called clueless.