\chapter{Journey to Shaolin (5)}

The embrace of a self-proclaimed mother was nothing short of warm. Although Qing was a complete stranger, the Empress was embracing the body of her daughter who had returned from death.

Qing wondered where this complicated story had begun.

Of course, it all started when she followed your advice, the strategy guide, trying to enjoy life a little without too much difficulty.

But what was wrong with that? Was it a big mistake to just want to watch the beautiful women from beyond the screen, cut down some enemies, make some friends, and easily follow the storyline to its conclusion?

She wondered if it was because only this body could handle those complicated settings, or if it was because this was a separate world created as is, or maybe her main body was beyond the sky and the screen, clicking away with a tired expression as always. Sigh. Let's not think such wicked thoughts...

Still, it was fortunate that she was in someone's embrace, and moreover, held tightly as if the person was trying to melt her into one with them.

Even if she thought wicked thoughts, she didn't have a seizure.

Just as Qing was thinking such thoughts-

"Alright, I've held you for too long. Then, now-"

This woman really doesn't know when to quit, does she?

This time, Qing squirmed in her arms, as she was in a state where she would have a seizure if she was released.

"Just a little longer."

"What kind of unruly behavior is this for a grown-up princess? You must know that you are not the same monarch you once were."

There are two ways to become a princess.

The first is to be born as the Emperor's daughter and then be appointed as a princess by the Emperor. (Therefore, not all daughters of the Emperor are princesses.)

This is because a princess is not just a term for the Emperor's daughter, but rather a title or position bestowed upon her by the Emperor.

The second way is to be born as the Crown Prince's daughter, be appointed as a monarch by the previous Emperor, and then naturally be promoted afterward.

Since Shaoxia had already received the title of monarch during the reign of the previous Emperor, she was naturally promoted to princess in the current Emperor's reign.

Therefore, the Empress's words meant, "You're not a child anymore, so what kind of unseemly behavior is this?"

Despite her words, she was holding her daughter so tightly that her mouth was practically torn to her ears.

Qing, too, enjoyed the warmth of that embrace without any resistance this time, and it seemed that bad thoughts melted away, making her feel invigorated.

"Then, now-"

"This time, I can't hold back because I'm starting to feel wistful. Let's stay like this for just one more hug."

Seriously, this woman really doesn't know when to quit.

Eventually, Qing was released much later, only after being allowed to change into new clothes after a very long time.

Even then, it was only because a loud, gurgling sound, like the earth-shattering death throes of a demon or a desperate scream from hell, emanated from Qing's stomach.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"The words of the martial artist, Cheonhwageom, to Her Majesty were very earnest. He professed that Shaolin is the leader of the Orthodox Faction and that they are righteous individuals of the human world who deserve to be fully respected. Her Majesty granted her permission, promising not to trouble you, so you should be grateful for her grace."

Although not quite as effeminate as a typical eunuch, the eunuch's womanly voice still made the listener doubt their eyes.

Apart from that, it was good news for Shaolin.

It was a declaration that they would no longer insist on entering and would obediently return.

It was also a gesture of goodwill, attributing it to Qing, whether it was a consideration or an act of meddling.

"Shaolin has once again received your help. You have spoken well of us to Her Majesty."

He was the greatest martial artist in the world.

If he wanted to, he could eavesdrop on the conversations inside the carriage by enhancing his hearing.

But would a monk eavesdrop on others?

Moreover, if the greatest martial artist in the world were to secretly eavesdrop on a conversation between women, it would be a shameful act deserving of public condemnation.

A master of his level should just summon a bunch of Force Compressions and demand that they tell him everything, using his martial prowess to intimidate them into submission.

It was not right to eavesdrop like a thief. That was what the Unorthodox Faction did. (The future of the Moyong Clan looks bleak.)

And if he had been caught eavesdropping, it would have been a grave sin.

But it would have been better if he had eavesdropped.

If he had, he would have realized that it wouldn't be detrimental to have Princess Shaoxia stay in advance.

And he wouldn't have thought of making her work without even feeding her.

"Well then. We'll be on our way before the sun sets. Let's go see the Absolute Sword Wall."

"Excuse me, Great Monk? Shouldn't we have dinner first?"

"Hmm. For starters, there is no meat in temple food. And I heard from Yuha that after seeing the Absolute Sword Wall, you vomited everything in your stomach. If you eat dinner and then see it, wouldn't you just vomit up all the food you ate? Is it respectful to the offering to vomit up the food you eat?"

"No, I just vomited some dead blood......"

Or did I? Maybe I vomited more than just blood?

It was so long ago that Qing's memory was hazy.

However, the Great Master's words were not wrong either.

If you're going to vomit after eating, it's better not to eat in the first place. But I don't want to be hungry. I should have insisted on having dinner with the Empress at Shaolin.

I feel like I've made a huge loss...

But his words about there being no meat in temple food really hit home.

What is the meaning of a meal without meat? Thinking about it that way, maybe it's a consideration to let me starve a bit longer so I can enjoy the delicious meat even more.

"I should hurry up and see it so I can eat. My stomach and back are about to dramatically reunite as a separated family."

"From what I can see, you could go without food for two months and still be fine, but, well, let's go."

As they were about to follow the Great Master, Seol Ri, who had been falling behind, came into Qing's view.

"Miss Seol? Where are you going? Weren't you going to follow me?"

"To eat."

Seriously, who's going hungry here?!

Qing examined Seol Ri's expressionless face.

She couldn't tell whether she was being teased or if she was just stating a fact.

I thought the distance between us had lessened a bit since she had poked me in the side and taught me the answer.

As she wondered if there was even the slightest hint of a smile mixed in, Seol Ri added a word.

"Meat."

"Ah, seriously."

I think she's making fun of me, right?

Seol Ri leaped away, saying she was going to eat meat, and Qing followed the Great Master, clutching her hungry stomach.

The Shaolin Monastery occupied the northern foot of Mount Song, and the Absolute Sword Wall was carved on the southern peak by the Celestial Martial Emperor.

In fact, thanks to that, Shaolin monks had to take turns guarding the Absolute Sword Wall on the southern peak every day. Considering that, perhaps it was a consideration to show it to female martial artists, not just a sacred place for women.

Thus, upon arriving at the entrance of a secluded valley leading to the Absolute Sword Wall, two Shaolin monks could be seen.

One was doing handstand push-ups, and the other was striking the sheer cliff with his fist.

"Tsk tsk. I told you to stand guard, but you're already slacking off."

"Ah, Abbot! I was just looking at it upside down, but I was still diligently guarding, ahem."

"Cultivation and Buddhism are one, ahem."

The Shaolin monks, who were trying to make excuses, turned red in the face as soon as they saw Qing's appearance.

And then they acted as if they had discovered something suspicious on the ground.

Hmm. So that was slacking off.

It was indeed slacking off to have one standing upside down and the other punching the wall when they were told to stand guard.

"Tsk tsk. So lacking in composure. If you were to brush against some flesh, you would surely renounce your vows."

"Brush against some flesh......"

"Namo Amitabha! Temptation! Temptation, begone!"

At that, one of the monks' posture became awkward, and the other started hitting the wall again.

Qing's gracious beauty was already at a level where she could be discussed as the best under heaven. Even the greatest Divine Art possessed by a Shaolin monk would be useless. Even if he was the best under heaven, he was still a third-rate man, so there was no way he could endure it.

"Tsk tsk. Let's go."

"Uh, yes. Please take care."

Qing greeted them and followed the Great Master into the valley.

And as she followed the steep path, stepping lightly with her toes, a wide basin suddenly appeared.

"Well then. What do you see?"

"Uh....... That cliff is split?"

On one side of the basin, a tall rock cliff was vertically split in a long line. The cut was smooth and straight, so it was obvious that it was not a natural phenomenon.

Could it be that that old man just split a cliff with his sword or something?

Previously, the Absolute Sword Wall of Mount Hua had been scratched by thousands upon thousands of sword forces, so even though it was marvelous, it was natural for sword forces to leave marks on rock faces.

However, the setting sun was shining through the split cliff, revealing the wonder of a huge rock wall completely split in half, all the way to the other side, facing due west.

"Now. Here. Do you see this footprint?"

The Great Master, standing in the middle of the clearing, pointed to the ground with his finger.

A large footprint was clearly and deeply imprinted on the stone floor, and around it, fine cracks spread out in a large circle, nearly three feet in diameter.

"Here, he stood like this, raised his sword, and with a forceful step, he cleaved the cliff. Try matching your feet to the print."

Qing obediently placed her foot inside the footprint.

Then-

\begin{quote}
[Encounter - The Legacy of the Celestial Martial Emperor]

[You have witnessed the profound insights left by the Celestial Martial Emperor.]
\end{quote}

Ah. Right. It was like this.

The world lost its color, turning completely gray.

Qing tried to find the figure of the old man shining brilliantly amidst it, but, huh? What's going on?

Why can't I move?

To be precise, it wasn't that she couldn't move, but that her body moved on its own.

Her field of vision automatically turned, and a monk, whom she had never seen before, came into view.

He must not be the Celestial Martial Emperor, as he was just a bald head in gray.

'Hey, baldy.'

Qing was startled.

No, I just thought about it, but I didn't mean to say such a rude thing out loud.

But the voice coming out was that of a gruff old man.

'Breaking the chains of reincarnation to enter Nirvana. Is the pursuit of Buddhism submission or defiance? They say that if you just wait patiently within the eternal cycle of reincarnation, the Maitreya of the infinite future will save everyone together.'

Maitreya Buddha refers to the Buddha who is already destined to descend in the future in Buddhism.

This greatly compassionate and infinitely virtuous future Buddha will descend and spread his teachings, leading all beings in the world to enlightenment and Nirvana.

For reference, this is the origin of the saying that a certain one-eyed bald man from the past used to mutter like a habit, claiming himself to be the Maitreya.

Anyway, isn't salvation already planned and decided, so isn't waiting quietly in the cycle of reincarnation the path of obedience?

That was what the Celestial Martial Emperor was asking.

The monk opened his mouth to speak, but his voice could not be heard.

And then the Celestial Martial Emperor replied.

'You call it immobility, but there is no difference between moving and not moving.'

At the same time, his right arm was raised.

Judging by the feel of the grip, it seemed to be held upright, but for some reason, the weight of the sword kept getting heavier.

Thus, after a long while.

A single, seemingly weightless longsword became as heavy as a boulder, a stone mountain, and then Mount Tai, pressing down on his raised arm, shoulder, waist, and foot.

Thus, at a certain moment, Qing could simply realize that she was supporting the weight of the entire world in this hand.

But immobility.

The Celestial Martial Emperor did not move.

But the world moved.

A huge cliff approached on its own, throwing itself before the Celestial Martial Emperor's sword.

The thing that moved was not the sword, but the world.

'You pursue the state of no-self, but I will shout that I exist in this world. Thus, I wish for human will to not be swayed by any destiny, to rise as a radiant sun with my own life and my own achievements. Thus, a person resists their predetermined fate and walks their own path. This is liberation, awakening, and the path of defiance.'

Thus, the Celestial Martial Emperor concluded.

'In the same logic as motion and stillness, if erasing oneself from the world to become non-existent is no-self, then erasing the world to exist alone is no different from self-existence. In other words, no-self and self-existence are one.'

The world, which could not break or crush the Celestial Martial Emperor, split in two, leaving only the Celestial Martial Emperor standing alone.

Alone, hence peerless.

Existing as oneself, hence self-existence.

\textbf{Solitary Nine Swords, First Movement.}

\textbf{Only I Am Supreme.}\footnote{唯我獨尊; Wei Wo Du Zun; Traditionally believed uttered by Siddharta Gautama when he was born.}