\chapter{Journey to Shaolin (1)}

In Zhongyuan, people held a special fondness for ranking and
classifying things.

In the ancient, primitive, and barbaric Zhongyuan, where
entertainment required money, this was perhaps one of the few forms
of amusement that could be enjoyed without spending a dime.

And since the Wulin Tournament was a grand event where one could
seize information from this greatest pastime, enjoyed by people of all
ages and genders, and enjoy it first, it was inevitable that people from
all over Zhongyuan would flock to it.

Thus, the hottest topic currently heating up present-day Kaifeng was
none other than Ximen Qing.

At the age of twenty, she had entered the Transcendent Realm, an
achievement even the great Celestial Martial Emperor had not
accomplished. As such, she was the greatest prodigy of all time,
literally a genius of history who had achieved such a feat the fastest in
this long era, starting from ancient times.

Therefore, regarding her martial prowess, they praised her as the
future Greatest Under Heaven and the current strongest among the
Rising Stars. Truly, she was the Hidden Dragon's Phoenix, the First
Among Hidden Dragons, and the Greatest Rising Star of the Central
Plains.

However, this alone was not entertaining.

The joy of ranking and classification came from the intensity of
clashing opinions, often escalating into heated arguments and
sometimes even physical fights where heads were cracked. Such
vehemence was necessary for it to be truly enjoyable.

Since there was no disagreement that Ximen Qing was an unparalleled
genius, the competitive instincts of the people of Zhongyuan
naturally turned to her beauty.

Qing usually had Tang Nanah by her side.

And for the past few days, Murong Juxi had also been clinging to her
like a cicada.

Thus, it was like volunteering for a comparison.

In Qing's hometown, it would be like a singer sticking to an actress;
separately, each was a stunning beauty, but when seen together, only
one woman caught the eye.

Thus, the flower among flowers, the most beautiful flower.

The Heavenly Flower among flowers, Ximen Qing!

It was virtually the title of the Most Beautiful Woman Under the
Heavens.

However, a great war erupted here.

The Five Flowers of Wulin each possessed their own unique charms.

Depending on tastes and preferences, each had their own followers.

In the first place, the Five Flowers of Wulin were classified as One
Center, Two Short, Two Tall.

Tang Nanah and Murong Juxi were among the Two Short, meaning they
were two of the shorter ones.

The followers of the Poison Flower and the Sword Flower preferred
petite and cute women.

Thus, even when they saw Qing, they thought that while she was
indeed more beautiful, she was too tall from top, center, and bottom,
making her excessive in all three aspects and thus not to their liking.

However, since the two had volunteered to stand next to Qing for
comparison, their followers had to acknowledge Qing's beauty.

Though not cute, they could still easily admit that she might be the
Most Beautiful Woman Under the Heavens.

However, the followers of the other three were still fiercely resistant.
First, the One Center. The Lily, Jinseol, who was neither too tall nor too
short, thus lacking distinctiveness.

Jinseol's charm was her breasts, rumored to be of the most perfect size
and shape. It was also the source of the Lily's confidence to boldly
flaunt her chest with a daring, low-cut hanfu.

The Two Tall. The two who were on the taller side.

The Frost Flower, a slender, cold beauty whose charm was amplified by
the alluring beauty mark by her eye.

The followers of the Frost Flower argued that although she was cold,
she would be warmer than anyone else to her man, a claim without
any basis.

And then there were the followers of the Wise Flower, who argued
that if a beauty was acknowledged by everyone despite her fierce
countenance, she must truly be the most beautiful of all.

Thus, the newly formed Ximen Defense Force and the followers of the
Poison Flower and the Sword Flower pushed Qing as the Most
Beautiful Woman Under the Heavens, while the followers of the other
three refused to acknowledge her as such.

And so, at first it was 'The Most Beautiful Woman Under the Heavens,
The Flower Among Flowers, Ximen Qing', but after countless fights
and cracked heads, it became 'The Heavenly Flower Among Flowers,
Ximen Qing', or Heavenly Flower for short.

Therefore, for Qing to be recognized as the Most Beautiful in Wulin, a
great effort would be required.

She would have to stick close to the other three and show off her beauty,
asking, 'Do you feel the difference in our power?'. There would be all
sorts of schemes and strategies, no doubt.

Of course, Qing didn't give a shit.

"Ha. What good is it for me to be pretty? My partner should be the
pretty one. Anyway, can I even see my own face?"

Qing's words were such that although it always felt new and thrilling to
look in the mirror, that was it. It was just annoying to have people
crowding around her.

Moreover, Ximen Surin had confiscated her veil, saying that she should
use her face to benefit the world and become famous, so she couldn't
even cover herself.

Still, Qing had no particular thoughts on the matter.

Men did not make a fuss like the followers of the Jade Qilin did. They
just turned their eyes like strabismus, bumping into someone or falling
over.

Besides, she had always been indifferent. She did not stop those who
came, nor did she hold onto those who left.

When meeting, be warm and welcoming; when playing, have fun; and
when parting, be cool.

It was a surprisingly common type.

People who did not contact first, making them seem like they were
ghosting, but who would also respond warmly when contacted.

Thus, she could not really understand Tang Nanah's glistening tears.

"When will we see each other again like this……"

"We'll see each other again if we happen to cross paths, won't we?"

"What? Are you not sad? Aren't you sad at all? We don't even know
when we'll meet again after we part now."

"Hey, I can visit the Tang Clan, or Nana can come visit the Divine
Maiden Sect. And the Five Flowers of Wulin are so famous that news of
you will spread far and wide. If I'm nearby, you think I won't come
looking for you?"

"Why are you talking like it's someone else's business? You're a Flower
too, you know? Add one more and it's the Six Flowers of Wulin."

"Isn't that still unofficial? Well, if you hear that the Transcendent,
Transcendent Qing has appeared, you can come find me, then."

"Ehh, sheesh."

Tang Nanah was still looking quite sad.

However, the Tang Clan had acquired the Blood Cult's Solitary Poison.

As one of the Tang Clan's most excellent poison makers, she couldn't
just neglect its research. Moreover, she herself was itching to learn
about the mysteries of the unknown poison as soon as possible.

So, as soon as it ended, she rushed off, saying she had to go study
poisons, and one by one, everyone departed for distant or near
destinations.

"Sword Bro, when we meet again, let's see each other as fellow
Transcendent Realm Masters, yeah? It doesn't really feel right to call
each other friends like this."

"Hmph. Just you wait and see."

The Namgung Clan headed to Anhui.

"It would be perfect if Qing'er could visit this time. The land of Hebei is
really cool. They say it's going to be hot this summer, so if you're
looking for a place to escape the heat, make sure to visit our family."

"Yes, Choryeo. Sanie, you have a safe trip too."
"See you later."

Sanie offered a casual farewell.

"Young Lady Ximen, if you ever pass by Jiangsu, please visit my home
in Nanjing, will you?"

"Oh. Nanjing. Nanjing. Why does that sound familiar? What's in
Nanjing? What's it famous for? Is it a good place to take Jangmyeong if
it's not a ruin?"

"Uh. Th-That. Nanjing is……"

Gong Sonye's shoulders slumped.

"Hot……"

Nanjing was known as one of the hottest cities in Zhongyuan.
Of course, there were deserts here and there in Zhongyuan, but
those were considered remote areas, not part of Zhongyuan
proper.

It was similar to how Koreans classified everywhere outside the capital
as the countryside.

"Eh, what's the big deal about it being hot? My affection for Ye is hotter
than that. Is our love something that can be overcome by mere heat?"

"Ah……"

As Qing held Gong Sonye's hand tightly, she thought to herself.

I hate the heat. I should not go.

After all, they would see each other again soon anyway.

Unlike Nana, the Rising Stars who lived close to the Wulin Alliance
were easily summoned. After all, even if people lived together in the
same room, the one who sat closest to the fireplace was the one who
would always turn it on.

And as a young Supreme Master, whom the Wulin Alliance would
undoubtedly promote, Qing was expected to do the same.

It was in line with Ximen Surin's wishes, who wanted to actively
promote her as the representative of female Masters and the first
female Greatest Under Heaven.

As such, there was no way for Qing to avoid it.

"Ah, I've been wandering around so much that my joints ache. Will this
disciple be able to massage my arms and legs this winter? Can I
receive your care, too?"

"Of course. This disciple will massage you thoroughly, so please make
sure your joints ache until then."

"You brat."

After a tour of the Absolute Sword Wall, they would return to the
Divine Maiden Sect to spend the autumn, and this winter, she planned
to finish the unfinished training of the Divine Footwork at the Hallim
Institute.

"Here. It's time to return it."

"Ah. That's right. My Bokshinjaeok."

Qing, who had completely forgotten about the treasure, was delighted
to see it. She had forgotten about it since she never had to play the
flute, and she didn't carry it around with her.

At that, Cheon Yuhak clicked his tongue.

"Honestly. To think you would just leave this precious thing and then
say 'Ah, that's right'. What a waste."

"Hey. I'm a martial artist, so what am I supposed to do with a flute?
Ah. Then, this should be returned-"

"Enough. You're a woman too, so carry a dagger. If any bad guy tries to
do something, stab him. It's the sharpest dagger under the heavens, so
you won't have to use much strength."

"Hehe, thank you."

Qing put the Blue Jade Sword back in her bosom.

Cheon Yuhak, who had to take care of his overdue academic duties at
the Hallim Institute, left with a grumble.

"Th-Then, Young Lady Ximen."

"Young Lady Murong. How is your health?"

"Thanks to you."

Murong Juxi had been doing a lot of thinking these past few days.

And she had made up her mind.

Until now, there had been too much hatred boiling inside her.

The harsh and horrendous torture, not just the pain, but the terrible
times that were designed to thoroughly destroy a person's dignity.

She felt like she would go crazy if she didn't vent it, that her insides
would burst and she would die. That was why her hatred had turned
towards Qing.

If you had come just a little earlier, if you hadn't made me experience
such a terrible dismemberment, I hate you, it's all because of you.

But now she had let it go.

Because she knew that it was a pain she would have to bear for the rest
of her life, that she would have to endure the agony that would
suddenly come to mind, and that one day, she would have to make sure
it was nothing but a scar. Though she didn't know when that day would
come.

The Ximen Qing that Murong Juxi saw was a monster.

When she was dismembering that living person alive, she felt it. The
depraved, almost lascivious thrill that seemed to ring in her ears. That
was why she thought she was a monster, and that she was allowed to
hate her.

But now, she thought she understood a bit.

Some people couldn't endure unless they went insane like that. She
thought that Young Lady Ximen, too, must have some kind of madness
that she would carry for the rest of her life.

And after that, she could see her kindness.

The kindness that allowed her to embrace others despite her own pain,
her benevolent actions, and above all, the warmth of her embrace, the
whispers that it was okay and that it would be okay. How much comfort
that had brought her.

"Thank you. For everything you've done for me. For saving me, for
leading me, for embracing me, thank you so much. I don't think I ever
said these words to you."

"Ah, now's the time to show off, isn't it? How hard I worked, huh.
Well, then, goodbye. We'll meet again someday."

Qing offered a cool farewell.

However, Murong Juxi lingered, unable to leave.

"Th-That. I know that I must endure it and that it is my cross to bear,
but if it ever becomes too difficult, if it feels like I'm the only one in
pain in the whole world, if it becomes too much to bear, could I
perhaps ask Young Lady Ximen for a small favor……"

"Hm? What is it?"

Murong Juxi's face turned bright red.

It was then, the cool, the way she gently bit down, with her fingernail,
pinching, the sudden thunder, how her entire body felt pierced, how it
felt like she would faint, the ticklishness. She couldn't move. I like it, this
kind of pain can help me heal the painful memories. Her voice. Her
cool touch, the beautiful whispers like a snake. Pinch.

"Young Lady Murong?"

Qing tilted her head, looking at Murong Juxi, who suddenly started
twisting her body like she desperately needed to take a piss.

What's wrong with her? Is it the summer cold? Even dogs don't catch
that, you know?

"N-No, it's nothing! It might, it might be okay, I was just, um, feeling
regretful, and now that I've expressed my true feelings, if you leave
now, then again, when, uh, um."

"Hmm. If it's really hard, you can recuperate at the Divine Maiden Sect.
I'll tell my master the whole story, and she'll probably let you stay
among the disciples."

"May I really do that?"

"I won't necessarily be at the Divine Maiden Sect just because you
come, but they're all good people. Ah. But if you cause any trouble at
the Divine Maiden Sect, the punishment won't be from me, but I'll
never see you again. Be good, okay?"

"Be good. Yes, yes!"

Murong Juxi steeled her resolve.

Be good, be good.

Then, when I meet Young Lady Ximen again, I'll tell her honestly and
ask her. She's a kind person, so she'll surely……

Qing tilted her head.

Is she still not feeling well? But her complexion looks really clear
compared to before. Hmm.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing joined the Shaolin monks heading to Shaolin.

Honestly, Mount Song was practically right in front of Kaifeng, a stone's
throw away, so there was no need for a schedule or anything.

Everyone was moving at a brisk pace, cultivating their Qinggong, so
they would probably eat dinner at Mount Song.

As she tried to keep up, making a loud 'thud thud' noise since she wasn't
used to moving at a brisk pace yet…

"Venerable Wolbong, do you still have any lingering resentment? I've
already let it all go, so if the Venerable has anything else to say, why
don't we settle it now?"

"N-No, no. There is no resentment. This meager monk's cultivation was
lacking, so I apologize, I am truly sorry."

"Venerable? Can you look me in the eyes and say that? Why are you
looking at the ground?"

At that, Venerable Wolbong looked at Qing, then let out a gasp and
stumbled, tumbling to the ground.

And then, he suddenly burst out-

"Urgh, this vexation! This vexation! Namu Amitabha……"