\chapter{Journey to Shaolin (3)}

\textit{What is this? Me?}

Upon seeing the pair of distinguished guests hovering above her head, Qing looked left and right, turning her head as little as possible.

\textit{I think they're talking about me?}

Qing slowly raised her head.

Honestly, it wasn't like Qing, who wasn't even from around here, felt particularly overwhelmed or didn't know what to do with herself. She just didn't like being the center of attention in this kind of atmosphere.

\textit{If she's the Empress, well, I'm friends with a Prince. Even though we haven't taken a bath together, nor slept in the same bed, but we have eaten together, so…}

\textit{If I had to say, am I something like the Empress's young brother's friend?}

To be precise, it wasn't the Prince's friend, but Ziyou's friend.

Qing looked up at the self-proclaimed mother of everyone in Zhongyuan.

Even though the backlight was shining on her, Qing's superhuman eyesight could clearly distinguish the Empress's face, which was
hidden in the shadows.

A very beautiful and noble lady.

It was difficult to guess her age just by looking at her face, as she had traces of time, yet her skin was still taut and youthful.

\textit{Well, if she's the Empress, I bet she spends at least two hours a day just taking care of her skin. I bet.}

Unlike Qing, who was just thinking about random things, the Empress's eyes trembled as she looked down at her.

"My child, what is your name?"

"I am called Ximen Qing, outer disciple of the Divine Maiden Sect, Your Majesty."

"How old are you?"

"I am of marrying age this year, Your Majesty."

"Hoo. Ximen Qing, Ximen Qing……"

And then, she just stared down at her, which was quite burdensome, before speaking again.

"You carry a sword? Are you a martial artist?"

"Yes."

"How much have you achieved?"

"It is embarrassing to admit, but I have only reached the Transcendent Realm a few days ago."

"Eunuch? What is the level of the Transcendent Realm? Is it commendable to have reached it at such a young age, or is it
something to be ashamed of for being late?"

"Your Majesty, it is an astonishing achievement, unprecedented in the history of Zhongyuan. If Your Majesty were not here, I would
have scolded her for daring to lie and deceive."

"Is that so? Then it is a very commendable thing indeed. I have heard many stories of the lives of martial artists, but I do not think I have heard how female martial artists live. I would like to hear about it this time."

And then, both the Empress and the eunuch looked at Qing silently.

\textit{What? }

Qing just blinked, and the woman beside her spoke in one breath, without tone and only with her breath.

-Her Majesty's grace knows no bounds.

\textit{Young Lady Xue! I see you're not a block of ice, after all!}

Having received the answer, Qing repeated it verbatim.

"Ah. Your Majesty's grace knows no bounds."

Thus, Qing followed behind the Empress and headed for the golden carriage.

As they walked through the crowd, all bowing with their bodies pressed to the ground, which was quite awkward, Qing took off all her weapons before boarding the carriage.

"A flute? Can you also play the flute?"

"Yes, Your Majesty. Although my skills are still lacking."

"Then there is no need to take it out. I would like to hear it as well."

"Yes, Your Majesty."

Honestly, to Qing, Fushen-di was more of a baton with an added function of making sound when blown, a very hard weapon made of
Thousand Years-Cold Iron.

After boarding the enormous golden carriage with the Empress, Qing realized that it was a space where only the two of them could face each other after all the attendants were dismissed.

She had asked to hear about the life of a female martial artist.

As Qing was carefully selecting what stories to tell, a shocking command suddenly came down like a bolt from the blue.

"Take off your clothes."

"……Yes?"

"Did you not hear me? I told you to take them off."

In an instant, a myriad of emotions crossed her mind.

What kind of bizarre command was this?

To suddenly tell her to take off her clothes as soon as they were alone.

Thankfully, she was a woman and a royal, but if she had been a man, Qing would have immediately struck him with Fushen-di.

'You're possessed by a perverted spirit! Be gone! Quiet down, you fool!'

Qing looked at the Empress in horror, but her eyes were only full of affection, without any hint of lewdness or other sinister intentions.

"I just need to check something, so do not be alarmed."

"Ye, yes……"

And so, Qing slowly took off her clothes. The Empress didn't even turn her head, just stared at her, which was a thousand times, ten thousand times more embarrassing.

After stripping everything off, the Empress spoke again, her voice trembling.

"Lift up your left breast."

"L-Like, like this?"

"Closer, th."

As Qing lifted her heavy lump of flesh, the Empress completely stopped moving, as if malfunctioning. Then, she suddenly reached out with trembling hands and stroked the lower part of Qing's left breast.

"Y-Your Majesty, this is quite inappropriate."

"There is a mole here. There is a mole……"

"A mole? There is a mole there?"

At that, Qing lowered her head and twisted it, trying to look, making a fuss as she lifted and pulled her breast, but she couldn't see it because it was hidden by the lump of flesh.

Afterward, the Empress continued to observe Qing's body from various angles, telling her to stand and turn around.

Then, suddenly, a tear streamed down her face.

"Your Majesty?"

"My child, do you not know? It is your mother. Your mother is here. This mother recognized you at a glance, but you cruel child, why do you not greet me warmly? Why do you do this……"

And then, she couldn't continue speaking as tears streamed down her face, causing her to sob silently. Qing could only express her
bewilderment. 

And then…

It took quite some time for the Empress to calm down.

As Qing was at a loss for what to do, she was suddenly pulled into a tight embrace, making her even more bewildered.

It was because…

To suddenly hear someone say something like 'I am your mother' sounded like a voice from outer space, making her wonder if this was really okay.

"Uh, I think you might be mistaken about something. Among the martial arts that martial artists learn, there are types that make one more beautiful. My appearance comes from that, so my original face was twisted and contorted, making me utterly hideous. Isn't it possible that Your Majesty is mistaken……"

Qing's beauty came from the Fairy Arts, or more precisely, from the transcendent charm ability points resulting from the increased stats of various martial arts she had learned.

When Qing first set out to Jianghu, she was so ugly that no one would even want to eat her, so it made no sense for anyone to recognize her based on her current appearance.

But the Empress was undeterred.

"A high fever caused by a strange disease made your skin fester and your face was twisted due to facial nerve paralysis. So, your once beautiful face turned ugly in an instant. Now that you have recovered, your original appearance has returned."

"No, that's not it. If I were really a Princess or something, there's no way I would have woken up alone in a cave."

"Are you talking about the cave at the foot of the western mountain in Liaoning?"

"Ah."

"Yes. They said that once you were revived, you would forget everything from your previous life and become a new person. Those
wicked priests did not completely deceive me with lies."

"Could you please explain it to this young girl in more detail……"

On the first day of the fourth lunar month, Princess Yeonseul fell ill with a strange disease.

All sorts of renowned physicians came and went, but there was no improvement.

Then, a Divine Doctor, known as the best in Jianghu, diagnosed her, saying that her brain was already dead, and she was just a living corpse. He said that in three days, her breathing would also stop, so they should prepare their hearts.

At that time, wicked Buddhist nuns from Tianzu, who called themselves priests of the Heavenly Maiden Temple, came to visit.

And so, they spoke.

Her soul and spirit have already reached the brink of death, so she is already a corpse, merely crossing the waters of the underworld while her body still breathes.

However, if her breathing is maintained for forty-nine days through a divine ritual, the name of the deceased can be deceived from the register of King Yama, the Great Underworld King.

Then, the soul whose name has been omitted from the register will return, and the dead will be revived.

However, since the soul has already been soaked in the Yellow Springs, all memories of the mortal world will be forgotten. Even if she is revived, she will not be the same princess as before.

At this, the Empress entrusted the princess to them out of motherly love, and they left for the sacred cave in Liaoning with two thousand five hundred gold coins and all sorts of elixirs.

And on the sixtieth day, she returned with the priests, her body healthy.

The Emperor and the Crown Prince were pleased and also admired their mystical arts, bestowing upon them the title of Imperial Palace Priests and writing the signboard for the Heavenly Maiden Temple.

"This foolish mother was deceived. Those wicked witches from the Tianzu must have presented a fake in your likeness. However,
the Emperor has long since lost his former wisdom and has fallen for the tricks of those witches. I came here to mourn the loss of my child, to pray for your peace in the afterlife, and lo and behold, thanks to Buddha's help, and his great mercy and compassion……"

"Uh………"

Honestly, it wasn't very believable.

If the mission window hadn't lit up, she wouldn't have believed it at all.

\begin{quote}
[Lineage Mission - Roots]

[You have encountered your true lineage.]

Drive out the fake princess and reclaim your rightful place as princess.
\end{quote}

The emotion Qing felt from that was relief.

\textit{Ah. So I wasn't something that suddenly assembled itself in the void, looking like a human, nor was I some sort of monster.}

\textit{I'm human. A real human being, after all.}

\textit{The original owner of the body I used to have was, well, brain dead, so was she a vegetable? Or something?}

\textit{When the mental parasite invaded, I confirmed that there was no other mind in me, so the original owner of the body had probably already gone to the afterlife a long time ago.}

Whether the protagonist of 'Life in the Martial World' that Qing chose originally had this kind of background story, or whether the appearance of her body just happened to match because she set her charm ability score to the lowest, thus resulting in her ending up in the body of someone who had become twisted and festered due to a strange disease, was unknown.

And she would never know.

If someone omnipotent had seen this, they might have clicked their tongue and asked who forced her to choose the Blood Poison Constitution with a knife to her throat.

And they might have asked if she had to choose it while forcefully summoning the Killing Star of Heavenly Slaughter, which had a long time left before its active cycle.

If Qing had heard that, she would have felt wronged.

Who would bother with such details in a virtual world enjoyed as a hobby?

And then, she became bewildered once again.

\textit{So, what am I supposed to say now?}

\textit{It would be awkward to say something like, 'Unfortunately, your daughter has already passed away. But don't worry, I'm using the body she left behind very well. By the way, if you're going to perform ancestral rites, please don't go to Shaolin. Can't you go to Emei temple where women are allowed to enter?', right?}

But she couldn't act all excited and say, 'Oh my, so you were my mother?'.

Regardless of anything else, Qing was not the Empress's daughter.

At least, her body seemed to be, but now that things had come to this, the saying that a person's identity lies in their memories felt incredibly poignant.

\textit{My mom is alive and well, not in this world, but in the other.}

\textit{But since she lost her child, she might not be doing so well, but I'm sure my older brother and younger sister must have comforted her.}

Then, the Empress stroked Qing's cheek.

It was a very affectionate touch.

"You are alive. My child. You are alive. Yes, seeing your face like this, thank you, just for being alive. This mother was guilty of not being able to follow you in death, but you are so beautifully alive and well. How truly commendable."

\textit{I'm about to really become a princess at this rate.}

Qing spoke with difficulty.

"Uh… I am truly sorry to say this, but this Heavenly Blossom Sword is already a disciple of the Divine Maiden Sect, living as the wanderer Ximen Qing, so the Empress……"

\textit{What should I say here?}

\textit{'Please pretend you don't know me'? That's weird.}

\textit{'I am not your daughter'? Isn't that even weirder?}

Qing was at a loss, no matter what she tried.

Then, the Empress nodded instead.

"Yes. That is for the best. The Imperial Palace is currently a den of wicked demons. It is truly fortunate that you are out in the safe secular world."