\chapter{Journey to Shaolin (2)}

"Oh my, Venerable Monk. Are you alright?"

Qing crouched down in front of the fallen Wolbong.

Qing's eyes curved prettily. Or perhaps, it could be said that they looked
bewitching and wicked.

"I, I am fine. Indeed, I am fine."

"Then why don't you get up quickly? Here."

Qing stood up and extended her hand.

Wolbong obediently took her hand and stood up-

"Gasp."

Suddenly, Wolbong abruptly jerked his hand away from Qing's,
avoiding her gaze with a somehow miserable, troubled, and
embarrassed expression. His posture, which had been in the process of
standing up, seemed to have frozen awkwardly.

"Venerable Monk?"

"Go, go ahead first. I will follow."

She must have thought he was embarrassed from falling while using
Qinggong. With a light tapping sound from her training shoes, Qing
caught up with the group of Shaolin Monks who had already gone far
ahead.

"Haha, that guy. Don't tease him too much, though. He must not have
realized it because he's only been in the mountains, but he's not used to
women. Please don't be angry if he's rude. It's all just a natural
phenomenon."

Is it natural to be such a greenhorn?

Qing tilted her head, but Wunue just chuckled mischievously and
muttered something ominous about adding twelve hours of horse stance
training.

But still, wasn't twelve hours of horse stance training an entire day?

Even for a Master, she felt like she should offer a prayer for his
well-being.

"By the way, is it okay to just leave that fairy like that?"

There was another member of the party, though it was hard to call them
a party.

It was Seol Yi-ri, who was following at a distance with her gaze fixed
solely on Qing.

"Well. Wherever she goes, it's Young Lady Seol's freedom, so I don't
think there's any particular problem, is there?"

"Wouldn't one usually ask to accompany them? She has quite the
unusual disposition."

Normally, when tailing someone, it was common sense to maintain
stealth and not get caught.

However, whether she thought she couldn't escape the eyes of the
Greatest Under Heaven or she didn't want to follow the common sense
of others, Seol Yi-ri was openly following Qing.

At any rate, from Kaifeng to Mount Song, it was close, less than three
hundred li1 in distance.

In Qing's homeland, even those weak youths without Inner Qi or
muscles would travel about a hundred li with a heavy load.

So for Masters, three hundred li was…

In the first place, it wasn't even a distance worth mentioning. If they
leisurely traveled with Qinggong, taking it easy for half a day, they
would arrive just when they were starting to sweat a little, feeling their
muscles tense a bit.

Of course, this only applied if one was a Transcendent Realm Master or
above, or if one was confident in their Qinggong.

As a result, Seol Yi-ri gradually fell behind, and the gaze that had
been tenaciously clinging to her was also left behind beyond the ridge.

But the attitude of Seol Yi-ri, who was less than a party member but
more than a stranger, was ambiguous.

So it was quite embarrassing to take care of her. After all, their
destination was Mount Song. Since such a huge mountain wouldn't just
run away on its own feet, she would probably follow along eventually
or something.

Thus, Mount Song!

Among the five famous mountains in Zhongyuan, known as the
Five Great Mountains, it was arranged in the order of east, west, south,
and north, namely Mount Tai, Mount Hua, Mount Heng, and Mount Heng.

Famous mountains were always occupied by Wulin sects, and these
were the sword-wielding Daoist sects known as the Four Direction
Sword Sects.

And Mount Song was the Central Peak. Because it was in the center.

If even Shaolin had used swords, the martial arts of all Five Great
Mountains might have been swordsmanship, but because of those
meddling bald monks, it was ultimately thwarted.

Thus, Shaolin Temple!

It was the most renowned temple in Zhongyuan. As well as the
center of the Orthodox Faction, it was also the number one sect under
Heaven.

First of all, the entrance to Shaolin, the mountain gate, had a great and
imposing presence. It looked more like a military fortress than a
temple, and its grandeur naturally evoked admiration.

And inside, starting with the famous Shaolin Temple's Welcoming Hall,
there were the Disciplinary Hall, the Eight Guardian Halls, the Hall of
Heavenly Kings, the Mahavira Hall, and the Sutra Repository. However,
Qing didn't know any of this.

Not only did she not know, but she also had no need to know.

After all, Shaolin was a sanctuary where women were forbidden. As
such, there was no point in knowing about it since Qing would never
see it with her own eyes in her entire life.

However, the Shaolin mountain gate was bustling with a large crowd,
and loud voices were exchanged.

"How outrageous! Her Majesty wishes to pray, so why are you
unscrupulous people blocking the way! Even if there are no laws in the
world, where is there a child who prevents their mother's entry!"

"Amitabha. Isn't Your Excellency already well aware of Shaolin's rules?
Please withdraw your words."

"What are you doing! Are you not going to open the way immediately!"

When Qing arrived, a not-so-fierce confrontation was unfolding
between the monks blocking the gate and the government soldiers
trying to break through.

It was accurate to say that it was not fierce.

The Shaolin Monks' attire revealed their rock-like muscles, with just a
single strip of kasaya draped over their upper bodies, exposing one
shoulder. Just by looking at them, it was obvious they were Masters of
External Martial Arts.

It was widely known that Shaolin Monks trained in both Internal and
External Martial Arts. As such, the Shaolin Monks wearing such
shameless clothes, allowed only for men, were Masters whom the
government soldiers couldn't dare to confront.

On the other hand, the Shaolin Monks also had no desire to see blood in
the sacred mountain temple.

Thus, a strange sight was unfolding, with the government soldiers
pretending to rush in and the Shaolin monks only pretending to push
them back.

"This is just. Ahem. Amitabha……"

Monk Wunue briefly murmured a Buddhist prayer before shouting,

"GAL!!!"

It was the original shout of the Shaolin Lion's Roar.

To clarify, gal meant to scold, so it was an expression that was similar
to shouting, 'You, punk!'.

The reason why they didn't just shout 'You, punk!' was because of the
face of martial artists, as one could become enemies by shouting such
things carelessly.

Originally, Lion's Roar was a term from the Buddhist scripture,
Vimalakirti Sutra.

Just as all animals yielded to the lion's roar, it was a phrase that meant
Buddha's teachings subdued all demons. Therefore, the Lion's Roar
was a term that referred to the great words of Buddha.

The Shaolin martial art, Lion's Roar, created with such an imagery, was
a profound music therapy, no, a sound technique, that had the ability
to clear away evil spirits from the mind and calm excitement.

With that pure and clear sound, the commotion stopped.

It was the Lion's Roar of the Greatest Under Heaven, so it was the most
powerful Lion's Roar among all Lion's Roars.

However, the one most affected by the Lion's Roar was neither the
Shaolin monks nor the government soldiers, but Qing herself.

Her mind suddenly became distant and a pain that felt like her
insides were being squeezed caused bile to rise from her throat.

What's this? Did I get indigestion? As she thought so, Qing's gaze
became particularly clear as she swallowed it back.

"Namu Amitabha. Everyone, this is a Buddhist temple. Even though
Shaolin has become secular, it is still a place where monks who have
nominally left the secular world chant Buddhist scriptures. So why
can't you keep quiet and instead, make a disturbance?"

"Abbot!"

"Great Monk!"

"Grand Master!"

The Shaolin monks' expressions brightened.

It was an expression akin to that of children who had found their
father while fighting among themselves.

Surprisingly, the government soldiers' expressions also brightened. It
was a calculation that, surely, he wouldn't order a suicidal charge
despite the appearance of the Greatest Under Heaven.

"Hmm."

Then, one person stepped forward with an arrogant tilt of his chin. As
his adjutant waved a flag, the government soldiers retreated from the
mountain gate and formed ranks behind him.

The person who stepped forward was arrogant and proud, but as soon as
he opened his mouth, his image changed drastically.

"This lowly one is called the Grand Secretariat Eunuch, Man Ri-hyung. I
am a humble eunuch serving the mother of all people under Heaven,
Her Majesty, Empress Chae. Her Majesty the Empress simply wishes
to offer prayers at the greatest temple under Heaven for three months
starting from today."

It wasn't the typical high-pitched tone of a eunuch, nor did it have a
woman's coyness.

However, his voice, which was closer to a woman's than a man's, did
not suit his angular face, which was trying to be masculine.

Regardless, what the Grand Secretariat Eunuch was saying was
anything but light.

It meant that the Empress, the mother of the Son of Heaven, had
personally made her way here.

Indeed, behind him was an extremely luxurious carriage, so dazzling
with its unique golden sparkle that it almost hurt the eyes to look at it.

"Ahem. Offering prayers is not determined by the size and fame of the
temple. Moreover, even if Shaolin is the greatest temple under Heaven,
it is famous for its martial prowess, not for its Buddhist studies. In fact,
we may even be a hindrance to the many renowned Buddhist monks. I
ask the Grand Secretariat Eunuch to consider this and withdraw his
words."

There's nothing special about offering prayers at a good temple. Since
you're here, why don't you consider going somewhere else?

"But since Her Majesty the Empress has come to offer her devotion,
how can you tell her to kneel in some ordinary, unknown temple? The
Imperial Family's grace has made Shaolin's virtue as high as it is, so
wouldn't it be good if we could share even a fraction of it?"

The Empress, no less, has come in person, so do you plan to just stand
there? And wasn't the land around here given to you by the Imperial
Family? When you received the land, it was the glory of the world, but
now that she wants to offer some prayers, you're backing out?

"However, the teachings of the Bodhidharma have forbidden the entry
of women. It is because we are foolish and stupid, unable to even
accept a woman's virtue. If you wish for the mystical virtues of a
temple of women, wouldn't the virtues of Emei in Sichuan be high?"

How can a woman's virtue have any effect in a place where only men are
present? If you want that, go to Emei. They specialize in women.

"Of course, I know that the words of the Patriarch are precious. But this
is the rule of monks, not the law of the secular world, is it not? How
can those walking the path of Buddhism so harshly reject lost
sentient beings?"

I know you guys secretly let women in.

So don't make a fuss and just let her in, will you?

In fact, the rule forbidding the entry of women was not a law
prohibiting them with a stamp and seal.

Shaolin's precept was more about not bringing women into the sacred
temple, as it was a rule that Shaolin monks had to follow.

Of course, even though that was Wunue's interpretation of the lenient
faction…

In fact, every year, three or four women, about one per season, would
enter disguised as men.

If one counted those who were caught, there were probably quite a few
who offered prayers without being caught.

"Ahem."

Wunue let out an uncomfortable groan.

Since it were devout commoners who had come with an earnest heart,
he couldn't punish them harshly, so he just scold them not to do it again and
sent them away.

Of course, it was a different story if it was a martial artist.

"That may be so, but how can it be that even though she wishes to offer
prayers, so many soldiers are mobilized, making it a spectacle for all
under Heaven to see? The rule of non-interference between the
government and Wulin must be upheld. The pure mountain temple
must not be used for other purposes."

Then, she should have come secretly. Why come so openly?

If she had come secretly, I would have secretly let her in to offer
prayers. The whole world is now watching and the Imperial Court clearly wants to make
it known that Shaolin's rules are being broken, so how can I let her in
now?

Thus, the prideful leaders' war of words continued tediously.

Of course, if one were a martial artist, they should fight with their
bodies instead of their mouths.

But if they fought now, the government soldiers would not be able to
avoid annihilation.

However, it wouldn't end with Shaolin saying, 'We won, we killed them
all'. Instead, they would have to relive the sad fact that history repeats
itself, with cannonballs pouring down like heavy rain. As such, they
couldn't carelessly resort to violence.

In fact, Wunue was already sensing defeat at this point.

Even if the power of the Imperial Palace was like a toothless paper
tiger, and the rule of non-interference between the government and
Wulin was upheld, they could not directly challenge the authority of
the Son of Heaven.

So it has become truly troublesome. It seems the Imperial Family is
once again revealing its ambition towards Wulin.

Perhaps another great bloodshed might occur in Wulin. Just as he
was sighing deeply at that vague premonition…

Click. And then, thud.

It was the small sound of a door opening, followed by the quiet noise of
something rolling and falling.

However, the result of that tiny noise swept through the area like a
massive wave-

"Her Majesty, Her Majesty the Empress has appeared! Show your
respect at once!"

At that, everyone, regardless of whether they were martial artists,
soldiers, or commoners, competed to bow deeply, pressing their
foreheads to the ground while holding their hands together above their
heads.

Qing, too, hurriedly followed Wunue, but then thought, 'Ah, this is the
monk way', and naturally switched to kneeling on the ground in a
profound bow.

Then, someone poked her in the side, so she turned her head to see
Seol Yi-ri, kneeling gracefully with her back arched, shaking her head
as if to say that wasn't it.

Ah, it's not a profound bow? Qing awkwardly adjusted to a formal
bow, following Seol Yi-ri's example.

In fact, Seol Yi-ri didn't know much either, so it didn't really matter
either way.

Bowing varied slightly depending on status, age, and gender, but one
thing was clear.

The Empress was the mother of all, so one should not dare to meet her
eyes.

Thus, with everyone quiet enough to hear even an ant crawling, only
the faint, powerless footsteps echoed in the mountain gate of Shaolin.

What's going on? It seems to be getting closer?

And then, a voice was heard.

"Child. Can you, can you raise your head?"