\chapter{The Showdown Between Humanity and Ximen Qing (12)}

Azhanke's expression contorted.

You idiot!

Why would you shout to the whole world that the skull is real?!

Sure enough, the bandits began to noticeably falter, turning to each other and muttering.

‘Was the leader really defeated? How are we supposed to deal with a bitch who beat a Master of the Unrestrained Realm?' and so on, spreading an aura of anxious whispers.

Qing poured oil on the fire.

"I won fair and square in a one-on-one fight! But then, surprisingly! Suddenly, he started begging, pleading for his life, saying he'd do anything, even cut off the head of the gang leader and offer it to me if I spared him! What a bastard, not even a real man!"

"D-Don't lie! Our Senior Brother would never do such a thing!"

"In the first place, Master or not, after a few hits, he was so flustered he didn't even use his Sword Force. I think he's just inexperienced in actual combat. He's probably just a has-been, spending all his days bullying the weak villagers. He was pathetic."

"Do not insult our Senior Brother! He is not such a person!"

"Oh yeah? Then how do you explain him losing to a Transcendent Realm Master?"

"You must have used cowardly tricks to ambush……!"

"Dou Sam did ambush me. But after I overcame that crisis and landed a hit, he couldn't even regain his senses. Maybe you're from the Liangshan Marsh? You should know, right? That Dou Sam's Invisibility Technique is amazing."

"That's……!"

It was an obvious statement, but history was written by the victors.

When the writers of history were wiped out so that only the victor's testimony remained, such a testimony became the truth.

As such, the truth of what happened between Qing and Dou Sam was whatever Qing said it was.

Of course, even considering that, it wasn't all that strange for a bandit to beg for his life.

No matter how great a Master of the Unrestrained Realm was, if he didn't want to die, he had to beg. Otherwise, would you just die if someone said, ‘Masters of the Unrestrained Realm shouldn't act so unsightly'?

"Well, is the gang leader there? Come out instead of hiding like a coward! Let's have a manly showdown! I see that being a Master of the Unrestrained Realm isn't all that impressive!"

If it were one-on-one, it was worth a try.

And if it didn't work out, well, she could just run.

It was also easier to escape if it was one-on-one.

In the first place, it was a fight between a Transcendent Realm Master and a Master of the Unrestrained Realm.

No one would blame the Transcendent Realm Master for running away.

Especially not if it was against a big shot like the leader of the bandits.

Even if she ran away after fighting such a big shot, it wouldn't be a blemish on her.

It wouldn't be considered honorable to not fight to the death, but no one would take it that seriously if someone ran away after not being able to win a fight against someone who was out of their league.

Conversely, it meant that a Master of the Unrestrained Realm had no real reason to fight.

It was too obvious that they would win.

But if they lost, they would become the laughingstock of the world.

Even if they didn't lose, it would still be embarrassing.

After all, how could a Master of the Unrestrained Realm, a peerless expert, not catch a mere Transcendent Realm Master and let them get away?

Moreover, even if they won but were injured, it would still be embarrassing.

What kind of Master of the Unrestrained Realm gets injured fighting a Transcendent Realm Master one-on-one?

However, Azhanke's heart sank.

Why is this bitch so confident, challenging a Master of the Unrestrained Realm? Did she hide her realm?

But it didn't make sense for a young girl, barely twenty, to have reached an even higher realm.

Maybe she really does have some confidence.

They say that one life-or-death battle is more helpful than a thousand fights.

Who knew when Dou Sam or the gang leader last had a life-or-death battle?

It wouldn't be strange if they were so rusty that they were unfamiliar with fighting opponents of equal standing.

"Elder Brother Shannoi, we need to bring the gang leader-"

At the sound of someone's inquiry, Azhanke freaked out and shouted before the words were even finished.

"No! We cannot! If we do that-"

"XI-MEN-QING-!!!"

But it was already too late.

Before Azhanke's dissuasion could even finish, a cry filled with burning hatred was heard, making his internal organs feel as if they were sinking.

As everyone turned their heads in the momentary silence, they saw eyes blazing with a bluish inferno approaching.

The killing intent was so palpable that it manifested as a visible aura, making the True Qi leak out in streams.

At this, the bandits of the Green Forest swallowed their saliva and lowered their eyes with solemn expressions.

Like a dangerous substance, the bandits parted to the left and right.

A pair of eyes, blazing like fire, approached.

Wow, what's that? It looks so cool.

To think that a Master of the Unrestrained Realm can shoot fire from their eyes.

I'm so jealous. I wish I could reach the Unrestrained Realm so I can do stuff like that.

Qing envied the other's ocular brilliance, not knowing that she did the same thing.

Moreover, Qing's ocular brilliance was the ominous starlight of Heavenly Slaughter, a type that humans instinctively knew and could not help but fear.

However, the primitive, uncivilized ancient China only had mirrors made from polished bronze, which were precious items. And even if they had one, who would look at their own reflection during a battle?

Qing's admiration was just that.

So, she just shouted casually.

"You have ears, don't you?! So you can hear me. Are you the gang leader!? Well then. Come here and let's have a proper fight!"

"Fine! You bandits of the Green Forest, listen! Catch that bitch! Alive!"

It was then.

SMACK!! With a loud noise, a bandit flew through the air and crashed to the ground.

"Did you not see me throwing stones? If you all come at me, I'll throw stones in the order you come. Let's see how many die while crossing the river. I'm telling you clearly. I'll hit you in the order you come. There are many stones here. They're everywhere."

At that, the bandits hesitated.

They had already seen the deadly stone-throwing in action.

How many stones would fly at them while they crossed a river that was fifteen zhang wide?

And in the order they came forward, at that.

So, they couldn't dare to take a step, glancing at each other, reading each other's faces.

If a historian were to see this scene, they would surely be filled with admiration.

A Great Hero, facing numerous bandits without backing down, truly befitting of the title.

Killing evil bandits with a single stone, a punishment from the heavens. Since it is a stone, let's say it's a meteor instead of lightning. They are both rocks, after all.

A Great Hero who throws meteors! Great Hero Meteor Thrower!

Originally, throwing projectiles across a river was a long-standing strategy from the dawn of humanity.

In any era of human history, and even in the future, it was considered the best defensive strategy.

The bandits of the Green Forest didn't even think about taking a step forward.

At that, Wang Cheolgun's solution was simple.

BANG, with a stomp of his True Footwork, Wang Cheolgun jumped sideways and split the head of an unsuspecting bandit.

"How dare you disobey orders! I told you to catch her! Immediately!"

Then, SWIIISH, SMACK! SWIIISH, SMACK!

Two more fell, spraying blood.

They were hit by stones, but they flew as if they had been hit by a carriage. In addition to the sound of stones flying and the sound of people being hit, the sight was visually terrifying.

The bandits of the Green Forest hesitated again.

Then, Wang Cheolgun chopped again.

Qing cheered inwardly.

This idiot is really doing all the work for me, huh?

What's this? Is he trying to help me or something?

If he keeps killing them here and there like this, that would be great. But the Master of the Unrestrained Realm, who was far away, was more frightening than the Transcendent Realm Master who was close.

Eventually, they would rush in simultaneously.

And then?

Then I'll just run.

Thus, after Qing had thrown stones to kill seven and Wang Cheolgun had beheaded three, a WAAAAAAH! Let's go! The forced and coerced shouts rose.

It was the signal to charge.

Qing ran away.

Wang Cheolgun, who had jumped across the water, chased after the figure of his enemy, but how could he find Qing, who had hidden in the dark, primitive forest?

"ARGHHHHH! XIMEN QING! XIMEN QIIIIING!!!"

Only the enraged cries echoed through the night sky.

"ARGHHHHH! ARGHHHHH!!!"

Not just cries, but he also kicked the campfire and overturned the pots, but if that was enough to vent his anger, he wouldn't have come all the way here in the first place.

The gang leader was beside himself with uncontrollable rage, his limbs flailing wildly.

And after a considerable amount of time, the ones who had some martial arts under their belt finally managed to cross the river.

It was too slow to be criticized.

It wasn't easy for even Masters to leap across a river fifteen zhang wide in one go.

Even without martial arts, no matter how swift, agile, and muscular one's legs were, a human couldn't jump more than three zhang at once.

Even if one knew martial arts, it was hard to jump seven zhang, and once one reached the level where that became possible, they could kick off from the water's surface, so there was no need to cross in a single leap.

At any rate, after that, the rest of the miscellaneous underlings crossed the icy water in the early winter night of November.

But alas. Qing had already left.

"ARGHHHHH!!!"

Wang Cheolgun's rage only grew louder.

Hearing that sound, the bandits of the Green Forest also felt their anger surge.

It's all because of that fucking bitch.

However, their anger wasn't solely directed at Qing.

But fuck, why do we have to suffer because of him?

If that Master of the Unrestrained Realm hadn't ignored the one-on-one challenge and forced people into the cold water in the middle of the night, would this have happened?

Even if she didn't run away, so what?

How are we supposed to capture the bitch who caught the leader of the Liangshan Marsh?

Not to kill, but to capture. Will she let herself be captured if we try?

Fuck, I'm so done with being a bandit.

Their morale and loyalty plummeted.

It was likely that more than a couple would run away and disappear after this night.

The reason it was ‘likely' was because Qing reappeared before the night was over.

They had crossed the valley, but there was nothing they could do.

Night searches were meaningless and only caused more harm.

Even if they stayed here, there was nothing to do, and the condition of the bandits, who were soaked in the cold night, began to rapidly deteriorate.

So what else could they do? They had to go back.

"It is clear that that bitch will reappear. Tomorrow, when the day breaks, have the elites lie in ambush on the other side of the riverbank. You, too, Gang Leader, should join the ambush. Then, when that bitch reappears like this, capture her."

"This is the last time. My patience has its limits, Azhanke."

"……I apologize."

Azhanke bowed deeply and apologized.

Though he wasn't truly sorry in his heart.

So they returned to their stronghold, lit a large fire to dry their wet clothes, and shared hot water, warm alcohol, and soup to warm their cold bodies, causing the stronghold to become noisy.

It was only very late at night that everyone finally laid their weary bodies down to sleep.

CLANGCLANGCLANGCLANG!!!

"You petty bastards! You're having a water party by yourselves and leaving me out? Is that fun?! I like water games too! I love splashing around!"

Qing lit another fire and made a racket by banging on a dented and broken pot.

The bandits had fallen into a deep sleep, exhausted.

Then, they woke up less than a shichen later.

They felt like they were about to die.

But what could they do?

They couldn't just ignore her and pretend she wasn't there.

Thus, they gathered at the riverbank again.

Only Qing shouted, feeling refreshed.

"Wang Cheolgun, come out! Let's do one-on-one!? Are you so scared of just one Transcendent Realm Master that you'll attack as a group? Hey, you, take off your dick, take off your cock! If a bastard who wants revenge for his son's death is going to be so calculating, then he probably wasn't that sad about it in the first place!?"

"You, you bitch! How dare you! How dare you!"

This time, the gang leader, who had come out early, trembled. His anger and frustration were beyond words, his speech was blocked, his hands and feet were shaking uncontrollably, and every word she spoke felt like it was scratching his heart.

It was truly extreme anger that made his insides twist and his teeth grind on their own!

And when that anger exceeded its limit…

It felt like all the blood in his body had drained out, and his anger turned cold.

"My son is dead. My precious son, whom I dared not touch for fear of bruising him if I struck him too hard."

His voice seemed about to explode at any moment.

"Do you think you even slightly understand a father's grief at losing his child? Even if the whole world points fingers, it does not matter. No matter how cowardly the method, I will make you die in the most horrifying way possible, no, I will make you live a life more horrifying than death."

It was a statement filled with such dreadful killing intent that it made the listening bandits' hearts grow cold.

But it didn't work on Qing.

"Ooh. Lowering your voice! Why, do you think lowering your voice makes you look cool? It really doesn't, you know? And if you're curious, ask politely! Do you not know any manners! Is your heart, the heart of a parent whose bastard children lost a bastard, curious! If you are curious, this lowly bandit would like to seek your esteemed opinion!"