\chapter{The Showdown Between Humanity and Ximen Qing (13)}

A fierce blaze ignites in Wang Cheolgun's eyes.

Oh, what's this? Does his structure grow bigger when he's angry?

"Words are useless, everyone-"

"Wait! Why are you trying to drag innocent people into a one-on-one? You're not confident, are you? You think you'll lose, so you're dragging your subordinates along, right?"

It was nonsense.

No one would willingly choose disadvantage over advantage.

If his subordinates could even slightly deplete Ximen Qing's stamina with a single swing of a sword, it would be a gain, as they could be replaced at any time.

And above all, he was not confident on his own.

He was not confident in capturing her alive.

He was barely suppressing the urge to split her in half right now. As such, if they were to fight one-on-one, he would probably tear her apart instantly.

He couldn't let that happen. Thus, wasn't he currently mustering all his self-control?

"If you do that, you'll die today. I promised my children that I would capture you and make you regret being born. A father who couldn't protect them must at least keep his promise."

Qing's eyes flashed.

"Wow! Look at this old bastard's words! Everyone! So, isn't he basically saying he's going to push his subordinates into a death trap just to make his revenge enjoyable? Wow, do you guys still call that a ‘Big Brother'!? What kind of Big Brother is that? He's just an old bastard!"

The bandits of the Green Forest could not simply ignore those words.

After all, wasn't he saying that it would be the end if they just killed her?

Wasn't this whole mess happening because they were trying to capture her alive?

Wouldn't they become enemies if they accidentally swung their swords and killed Ximen Qing?

Wang Cheolgun realized his mistake too late.

But if he did not engage in a one-on-one, it would be the same no matter what excuses he made.

Afraid? You're a coward.

It's for an advantage? So you're going to let your subordinates die to gain an advantage? What kind of Big Brother are you?

Trying to capture her alive? It would lead to this.

He had made the wrong choice from the start.

Giving up such a long tail to an expert at catching the tail of words meant that no matter what he said, the only way to deal with such an annoying bastard was to ignore them and say, ‘You keep barking, I'll do what I have to do'.

It was already a loss to engage in conversation like this.

Wang Cheolgun realized this a beat too late.

"I see no value in responding. Everyone, charge and capture that insolent-"

"Wait! Let me say one last thing! I'm innocent! It seems like you think I killed your children! I didn't kill them, so why is the premise that I'm your children's enemy!?"

Wang Cheolgun, who had decided to ignore whatever she said, was struck by words he could not ignore.

"What? You did not do it? You, did not harm, my children?"

"Wow, seriously. Let's go over it, starting with the first young master. I promised to spare his life, and I kept my promise, okay? I just broke both his shoulders, broke his legs, and removed all his fingers. But I didn't kill him, did I?"

"You, you bitch, you call that speaking."

The bandits who were listening were also dumbfounded.

So how could their father feel any differently?

Regardless, Qing continued her argument.

"Why would I provide treatment to a bastard who tried to rape me? He was crying and begging for his life, really wailing. It was pathetic. The eldest son of the Green Forest's Chief was on the ground, begging for his life, crying like a baby. He was truly a pathetic sight. So, I decided that such a pathetic bastard didn't even deserve my blade, so I let him go. Then he ran away and fell into a puddle and died on his own."

Flicker, flicker. The light in his eyes burned.

"When I saw him in the morning, he was dead, stuck in a puddle. Oh, but you know what? His belly was sticking out like a pregnant woman's. Since his limbs were broken, he couldn't get out, so maybe he tried to drink all the water in the puddle to escape. But how could he drink it all when it was pouring rain? Isn't that hilarious? It's like someone drowning in a river trying to drink the entire river."

The Chief trembled.

Suddenly, the scene vividly appeared before his eyes.

His son, thrashing with broken limbs, desperately drinking muddy water to survive, to be saved.

"The second one is really, truly unfair. I didn't touch a single hair on him. He was pushing his subordinates forward to die, and then he ran away in such a hurry that he tripped over a rock. Honestly, I don't know how he was running so fast, but he flew like ten zhangs and crashed into a boulder. Like this! Bam!"

Qing struck her palm with her fist, making a loud, sharp sound! that could be heard clearly even across the river.

"Come to think of it, wasn't he just like his father? He's pushing all his subordinates to die, trying to capture just me, isn't he? I wonder who he learned such cowardly behavior from. Oh right, he learned it from his father. Anyway, I'm really innocent when it comes to the second one. The first one might have some moral responsibility, but the second one died because he was scared and ran away on his own."

"I'll kill you!"

Qing hurriedly shouted.

"Wait! You have to hear me out! The virgin forest, I mean, your daughter."

The foot that had been raised to stomp the ground in preparation to leap forward landed powerlessly with a thud.

My daughter, my daughter.

"Didn't you see your daughter's corpse? It was carved on her belly and back. ‘I am the Demon Lord of the Blood Cult, Eon Yeonyoung'. So why are you saying I killed her and calling me your enemy?"

"You bitch! It was you! If not, how could you know that!"

"I won't tell you. You want to know? If you want to know, it's 500 taels of gold."

Qing held out her hand nonchalantly.

"You bitch! You did it! The fact that you know proves it! Ugh, ughhh. You bitch, you did it!"

"Ah, perhaps you don't even know how she died? It was a miserable death, befitting a bitch who ate people's flesh alive. She screamed for her life. I wonder if she called for her father in the end? Daddy, save me, Daddy please! Daddy, you said you'd protect me! What was the father doing then? You killed her! You killed your own daughter, you old bastard! Why are you looking for revenge from me when you killed your own daughter!"

Wang Cheolgun's eyes shed tears of blood again.

A bluish demonic aura began to mix with a purple venomous energy, gradually flowing out in dangerous colors.

Regardless, Qing continued to blabber on.

"In conclusion, I think it's unfair that you're blaming me for your children's deaths. Honestly, didn't they all die of natural causes? If a bastard does bad things and dies, then he must have died because he received divine retribution!"

"You, youuuu!"

"I'm going to heaven when I die anyway! Unlike your children! Do you know that murder leads to the Hell of Knives? Your children are suffering even in death! They'll be screaming for thousands of years as their flesh is eaten alive! If you miss your children so much, just die! Their father will go there too, so you'll have a family reunion in death, won't you!"

"I'll kill you!"

Wang Cheolgun finally exploded.

The pair of burning demonic auras shook violently and rapidly approached.

Qing knew from her experience with the Water-Gliding Steps just how difficult that was.

When Qing was asked why she had challenged the Water-Gliding Steps so many times, she would say, because one can run on water, so how could I possibly resist?

Anyway, the Water-Gliding Steps required one to strongly kick off the entire sole of their foot at once, demanding a very high level of concentration.

That meant it was a vulnerable moment.

So, Qing threw her hand with all her might.

Swish, with a powerful sound, a straight line stretched out like a taut rope, the secret technique of the Chivalrous Meteor, which she had demonstrated many times before.

However, Wang Cheolgun was a master of the Unrestrained Realm.

A mere rock? He could just take a hit.

Wang Cheolgun visibly activated a distinct Protective Qi around his entire body and slightly shifted his body.

Thus, Swish, Thud.

A blade smoothly penetrated below his shoulder.

Thunk. Unfortunately, it wasn't a rock but a throwing knife, that too, a barbed throwing knife that wouldn't come out once embedded.

I was worried that the Protective Qi might be pierced or not, so I sharpened the blade with great care.

But you're worried about the Protective Qi?

Think about whether your strength was lacking or not.

If a rock was enough to break someone's head, throwing a dart or a throwing knife would obviously be much more painful and have greater destructive power.

So why did she throw a rock?

Because if you keep throwing rocks, they'll think you'll keep throwing rocks.

Qing's aim had been on point.

As soon as the blade pierced his forearm, Wang Cheolgun's bluish light dimmed and fell.

Splash! The sound of a heavy object falling into water.

She was aiming for the heart, but his quick reaction made it go astray, and only thanks to her incredible level of control, no, her ability to throw, was she barely able to hit him.

"I hit him! Reverse, full-count! Ximen Qing scores four points!"

If anyone heard this, they would know that Qing didn't know baseball.

Because, you know, I don't know baseball. I don't know baseball.

I wonder if I can make even the Giants win at this point?

There's no problem with stamina, so controversy over shoulder overuse and whatnot can be ignored. I can just be the sole starter and make all the other players quit.

Well, the more you use your shoulder, the stronger it gets, right?

Qing looked at the surface of the water.

A master of the Unrestrained Realm wouldn't drown just from getting stabbed in the forearm with a throwing knife.

Is he planning something?

Is he going to ambush me if I get close?

At this, Qing recited the forbidden spell that could revive even the dead, the law of the Reanimated Corpse.

"……Did I get him?"

Then, Splash! A pair of eyes shot up high into the sky, spurting water.

It really was ‘Did I get him?!', huh? How effective!

Here comes the one-on-one that Qing had so desperately wanted.

Drawing the Moonlight Sword, Qing shouted triumphantly.

"Now, come! I'll give you a handicap of three moves because you're young! You're an Unrestrained Realm, right? Can't you give a handicap to a mere Transcendent Realm? You're such a petty bastard!"

"Shut up! I'll kill you!"

"Before, you said you'd keep me alive, but now you're saying you'll kill me! Oh my, all you bandits, did you see that? This bastard changes his words with every breath he takes!"

"Dieeee!"

Though drenched and looking ridiculous, his skills were genuine.

Wang Cheolgun, soaring high into the sky, suddenly changed direction at a sharp angle and shot towards Qing like a meteor!

What the fuck? How does he do that in mid-air?

Startled, Qing immediately took her stance.

She split into eight figures, running, flying, crawling, and spreading in all directions. As she did so, Boom! Wang Cheolgun's huge hammer struck the ground.

The earth surged up nearly a zhang high!

And behind it, a translucent Qing, who had been crawling on all fours, subtly appeared, erasing her transparency and turning her back.

But only for a moment, as she immediately turned around and widened her eyes.

What the fuck, is that really a meteor falling? What's with that crater?

So that's what a meteor strike is. Wait, no, was it me who became a meteor?

Is it a Bandit Meteor Strike?

Fuck, that seems incredibly strong.

But she had already made a commitment.

Qing gritted her teeth.

This is it, huh? This is really the Unrestrained Realm.

Not some novice in the early stages of the Unrestrained Realm, but a true martial artist who had properly entered the Unrestrained Realm.

What's with this ideology? Why isn't science being used?

This is why the basic scientific standards of Zhongyuan are so fucked up!

Masters of the Transcendent Realm are truly not human.

They can fly on swords (Sword Flight), walk slowly on water (Crossing Water on Reeds), and use telekinesis to pull people and objects with their hands like Jedi from the Space Age (Vacuum Snatch).

Transcendent Realm?

Transcendent Realm creates starlight.

In between, the Unrestrained Realm is actually a bit ambiguous.

Compressing Force is much stronger?

They have a long-range attack called Force Compression, but it's not as good as wrapping it around a weapon.

However, when it comes to a fight between a Transcendent Realm and an Unrestrained Realm, the gap is as great as that between a First-Rate and a Transcendent Realm.

Because in the Unrestrained Realm, a martial artist finally enters the realm of ideology.

Establishing one's own martial arts and walking one's own path. In the words of the Celestial Martial Emperor, it was a level where one could just barely swing a sword, just taking the first steps.

This is the act of twisting the laws of the world with one's own interpretation. It is the stage where an individual's ideological domain is drawn into the world through martial arts.

Creation means the principles of all things, and the reason why the world is as it should be.

It is a realm where an individual's martial arts reach into such principles, manifesting as an undeniable truth in the universe.

That is why it is called the Creation Realm.

It is commonly abbreviated as the Unrestrained Realm.

If one establishes their principles with their martial arts, it is the Unrestrained Realm.

If the principles of martial arts wield the individual, it is called the State of Demonic Deviation, or simply Demonic Deviation, and it is considered half a step below the Unrestrained Realm.

To overcome this, one needs a much greater realization than the Unrestrained Realm, and a martial artist closer to ideology is born. As such, the next realm, the State of Transcending the Demonic, is considered half a step above the Transcendent Realm.

"Uwaaaak! Ximen Qing! I'll kill you!"

A cry that seemed to boil the blood broke Qing's astonishment.

Qing retorted without losing ground.

"Why are you talking informally! You're a dying old bastard, so shouldn't you be politely asking a promising youth like me to kindly allow you to pass on? You should be respectfully requesting, not- Waahk!"

Before she could finish, the hammerhead fell like a meteor again.

Qing split into eight directions once more.

The Eight Trigrams Microscopic Steps was also a martial art that touched upon ideology.

Originally, it was a movement technique that was difficult to even imitate at Qing's level.

However, Qing's method of using martial arts was the biggest scam under the heavens, so she could use it very well.

Boom! The earth overturned again.

This time, Qing was crouching with her back arched and both arms extended backward.

As she subtly materialized out of thin air, she struck a cool pose, standing with her back to Wang Cheolgun as he slammed his hammer down.