\chapter{The Showdown Between Humanity and Ximen Qing (7)}

As she entered the bath, a cloud of hot steam enveloped her body, and the humid warmth seeped into her nose, reaching deep into her chest.

Ah, this is it. This is what I've been waiting for.

"What? Who is it?"

"Don't mind me, just soak that dirty body of yours. Ah, do you have any scented soap by any chance? If not, do you have any powder made from the root of the iris, or perhaps rice water? It doesn't cleanse as well, but… Well, if you have it, please let me use some."

Scented soap was the most luxurious beauty soap in Zhongyuan. Iris root powder was somewhat cheaper but still expensive enough that commoners couldn't even dream of using it.

‘Hwijup' was the juice of the fruit of the Gleditsia plant, while ‘ban' referred to the water used to wash rice.

It was almost as if she had entrusted them to her.

"What? Who are you? How dare you be so insolent when you don't even know who I am?"

"You watch your mouth, too. Who are you to talk down to me? You think you're so great just because you're the daughter of some bandit?"

The woman shut her mouth with a gasp.

This was a common trait among those who were considered part of the Unorthodox Faction.

If someone was more aggressive and forceful, they would shrink back, thinking that the other party might be someone of high status.

Thus, the woman's mind spun rapidly.

Who is she? Who could dare to call me the daughter of some bandit?

A female expert from the Unorthodox Faction?

However, even if she was a female expert from the Unorthodox Faction, her words were a bit too harsh this time. After all, it was practically calling Nokrim's Supreme Commander a mere bandit.

"Ahem. May I ask where you are from-"

"Enough, I asked you a question. Do you have scented soap?"

Reading the hesitation of the woman, Qing pushed harder.

And so, a stammering answer returned.

"T-There. On the shelf over there……"

"Oh, you really do have some? These bandits sure are rich. Where did you get this precious scented soap? Wow, it's quite large too. You must have paid a lot of gold for this, huh?"

Most bathhouses with a complete setup had a similar structure.

Three stone pits, one for hot water heated by a fire, one for room temperature bath water, and a warm water bath in the middle, where the temperature could be adjusted by opening and closing the water flow from either side.

It was common sense to wash oneself before entering the bath.

Qing grabbed a bar of iris root powder and scooped up a large amount of hot water.

Is it too hot? But well…

Qing had the Ice Arts.

Although its power was not that great, there was no better martial art when it came to cooling down hot things.

Thus, pouring the appropriately warm bath water over herself, she began to scrub vigorously.

"Ah, this is, truly, this is really… This is what life is all about."

The woman was dumbfounded.

Just who was she to use someone else's bath, someone else's water, and someone else's scented soap to wash herself?

However, if she thought about it, the guard outside, the 29th ranked member of the Yangsanbakdae(Sunshade), Cheonjoi, was guarding the bath.

Someone of a status that was not high enough would not have been allowed to enter without permission.

Furthermore, her natural way of speaking and the fact that she did not seem to pay any attention to the woman made her wonder if she was actually someone of high status.

It was uncomfortable to speak and she felt like she would lose if she left, so…

As she hesitated, the intruder, who had been scrubbing herself vigorously, finally emerged and soaked herself in the bath on the other side.

But her beauty, even the woman couldn't help but stare at Qing for a moment, despite being a woman herself. She had never imagined such a beautiful woman existed in the world.

Regardless of that…

Qing tilted her head.

"Hey, the water is so lukewarm. What kind of warm bath is this? It's just a lukewarm bath."

Then, she opened the sluice gate of the hot water bath.

Not long after, as the water temperature rose to a scalding level, she closed the gate in satisfaction and leaned back, letting out a strange sound like, "Aaaah, this is so nice."

"Excuse me."

"What? Why?"

"Uh, who are you……."

"If you must ask, I am Ximen Qing."

"Ximen Qing!"

The woman leaped up, making a high-pitched sound.

She wasn't even close to being friends with her. In fact, she had thought, ‘Good riddance' when she heard the news of their deaths. But at any rate, this woman was their enemy!

However, the moment she stood up, the other side of the bath was suddenly filled with flesh-colored skin.

"Ooh. A primordial forest."

"You, how did you get here, y-you came to kill me! Guard Kang! Warrior Kang!"

At the same time, she turned her body, so Qing grabbed the woman's hair and pulled her back.

"Kyaak!! Let, let gooo."

Amazing fact number one!

When a person's mouth is filled with water, they cannot scream!

Of course, they can make sounds, but the unique properties of the medium might prevent the sound from being transmitted.

However, at times like these, making a scientific approach would be something that those tactless STEM nerds would do, interjecting into conversations to distinguish between truth and falsehood.

Qing, full of liberal arts sensibilities, decided to just marvel at the amazing natural law she had just discovered, as well as the ecology of humans.

Qing pressed the woman's head into the bath and applied force. Actually, she didn't even apply much force.

After all, Qing's strength was already beyond that of a human, capable of crushing even a bear in the water.

At that, the woman thrashed around excitedly in the water.

Such forced submersion was originally a game that both Eastern and Western children inherently engaged in since childhood.

It seemed the woman was also enjoying the return to her childhood innocence.

She was so excited that her movements were very intense, splashing water everywhere.

How delightful it is to see her enjoy it so much.

After counting to thirty in her mind, Qing pulled out the head.

Without any force, the head naturally emerged with a vigorous bounce.

Then she let out a sound that resembled someone who had just finished a hearty bowl of soup.

Wow, that's quite a soulful sound.

Do you know how to enjoy soup?

There's no kimchi, so I'll offer you a bath instead.

Wouldn't you say it's almost like a Beauty Bath?

Since once isn't enough, she dunked her again.

Splish splash, it was time for some exciting water play.

One, two, three…… thirty.

Qing pulled out her head again.

Gasp pant wheeze. She greedily inhaled the air.

Qing looked at her handiwork, the woman's head.

Three hundred eighty-three points.

Through the ‘Tell Me Everything You Know' moment of truth, she had heard all sorts of stories.

Among them was information about the peculiar eating habits of the Supreme Commander's daughter, so seeing her Karma score, it seemed this was the very daughter of the Supreme Commander who ate people.

Cannibalism was not uncommon among bandits.

The woman had been exposed to it since childhood, so she didn't even know what the problem was.

However, she did enjoy fresh sashimi, so those who enjoyed dishes made from freshly caught ingredients were quite rare, even among bandits.

There was a divide in preferences even among bandits.

There were those who could provide the occasional fresh catch since she was a fairly beautiful woman and the daughter of the Supreme Commander.

And there were bandits who shuddered and called her a horrible bitch, saying that no matter how pretty she was, that was just not right.

Even her closest guard, the late Warrior Cheonam, who was chosen because he was the ugliest and therefore the least likely to catch the daughter's eye, shuddered at the thought of catching people and turning them into sashimi.

She felt a little sorry for the Supreme Commander.

She had belatedly learned through the ‘Tell Me Everything You Know' that the young man and the young man were brothers.

Well, if the siblings are all like this, it was clear what kind of family upbringing the Supreme Commander provided.

How could the first, second, and third children be a rapist robber murderer, a rapist robber murderer, and a cannibal murderer?

Then isn't it their own fault for being like this?

So, water torture, ah, no, water torture, I mean, water play twice isn't enough to quench her thirst for revenge.

It's not enough.

After all, the Korean sentiment is all about the rule of three.

She dunked her again.

Wow. I'm really being generous today.

I'm giving you one more for free.

And she dunked her again.

Oh my goodness. I'm giving you another one on top of the bonus!

One plus one!

She dunked her again.

Today, the owner has truly lost her mind!

Wow! It's cheaper than getting dunked!

Of course, I'm comparing it to expensive luxury brands like the Western Regions' Wisdom God or Golden Goose, but if you compare it like that, my dunking is also a luxury brand, you know?

Submersion!

Even if I sell immersions, I won't sell my conscience.

This is because my conscience is so precious and expensive that it's too wasteful to use it on you suckers.

Dip!

To be precise, there's no such thing as a dip, you know? It's just that a little water got in, that's all. Since it's thoroughly washed with water, isn't it actually better?

What? You're not buying? You're just looking? Loooooking?

Sir, this is really a problem. Ah, my fist is crying. I really can't beat you up. Fuck!

She dunked her again!

Wow, I'm really going all out today.

What will be left if I give away so much?

Nothing will be left. I'm going out of business.

I'm closing down the store. Going out of business. Cleaning out the warehouse.

Dip. Dip. Dip.

Finally, at the end of the long playtime, the woman, who had thoroughly enjoyed playing in the water for the first time in a while, leaned against the bath, exhausted and limp.

"Save, guheuk."

Since she had drunk too much water, her stomach was sending protest letters in the form of burps.

"And you're burping in my face? How were you raised? Ah, right. The daughter of a bandit. I can understand that, but I can't forgive you! Water creates manners!"

"Hieeek."

At that, the woman, despite not being able to control her body, thrashed and splashed, then somehow managed to crawl out of the bath.

Even out of the bath, she was so exhausted that she couldn't move properly. As such, she fell with a loud thud and desperately crawled on the floor.

"You have ten seconds to come back. If you don't, you'll be dunked ten more times. One, two, three……"

"Hieeek."

At that, the woman shuddered and desperately tried to stand up, taking two steps before falling with a loud thud! and rolling on the stone floor.

It seemed very painful.

But, she was trying to run away? How impertinent.

The ominous shade spread across Qing's eyes.

I was just trying to play with her a bit before killing her, but now I have to go outside the bath. How annoying.

But if she was left alone, she would indeed run away.

She may not get far, but if she makes a ruckus in the neighborhood, it would be a waste if the few remaining weaklings ran away.

Qing lifted her heavy behind and stepped out of the bath, grabbing the woman's hair.

"Argh, please! I was, I was wrong!"

"You should have begged before becoming a bitch. Did you ever once spare a living person when you were enjoying the pleasure of your tongue?"

"I won't do it again! Guheuk, I won't do it again, so."

At that, Qing firmly shook her head.

"Anyone can regret after fucking up. That's not remorse, it's just regret. So you should have reflected and corrected yourself before fucking up. Still, cheer up. I'll make sure you can live if you try hard enough."

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

In the past, Qing had once asked for help from an outstanding intellect that could represent an entire administrative region.

Thus, the intelligent one willingly helped Qing with her brilliant mind, and Qing learned a great deal in the process.

Thus, the teaching of the greatest intellect in Seongbushi.

If you want to throw an organization into chaos, burn it.

Burning is the best.

However, it was the No. 1 Stronghold of Nokrim, located on the bedrock between Cheonjabong Peak and the neighboring peak.

Moreover, from the mid-slope of Mount Cheongja, a thick fog made it difficult to see even three steps ahead.

Even if a fire broke out, there was no way to notice it from below.

Thus, the news that ‘your house burned down well' was delivered two days later.

On that day, the sun had set, so everyone withdrew and had a good night's sleep.

After all, there was no point in conducting a night search in Wŏn'gajie, where even in the daytime, no one could see properly, making it meaningless.

Moreover, after eating a late dinner, they lit a fire in the barracks for a warm night's sleep.

Since Ximen Qing was only losing physical strength in the damp and cold jungle of Wŏn'gajie, it was a decision that would make the long-term battle more advantageous for them.

Thus, if it were not for the chores group that returned to the main base to retrieve supplies the next day, the news of the fire would not have been known.

And Wang Cheolgun only heard the news after returning from an unsuccessful search.

The No. 1 Stronghold of Nokrim. Almost completely burned down.

"Say, say that again!"

"That is, someone seems to have set a fire……"

"What about Lani? How is Lani!"

The Mountain Lord A'jandeok watched the Supreme Commander.

"That is… Unfortunately……"

A'jandeok was on standby at the base, so as soon as he heard the news, he immediately mobilized the reserves and rushed to search the main base.

However, there was no need for a search. It had burned down so cleanly.

The No. 1 Stronghold of Nokrim was the headquarters of Nokrim.

It was originally designed to be thoroughly prepared for fires, so it was designed in a way that a fire in one building would not spread to the next.

This meant that someone had gone through the trouble of moving from building to building and setting them on fire one by one.

In other words, it meant that someone had set the fire.

Among them, only the bath remained intact.

The Young Lady was hanging on there.

Upside down, with only her head submerged in the bath.

It was a truly horrifying display of cruelty.

She must have tried to breathe by bending her waist until she ran out of strength.

One could only imagine how much she must have screamed for help.

And between the fear of death and the pain that felt like her body was being torn apart, she must have endured and endured until eventually…

A'jandeok did not reveal the details.

"Which, which bastard! How, who! Ximen Qing! Is it that bitch again?! It must be her, right?! Surely, it can't be, tell me it's not!!!"

The Supreme Commander screamed like a madman.

If his most cherished daughter was harmed by the same enemy after losing two of his sons, he felt like he would truly go insane.

Fortunately, A'jandeok fulfilled that wish.

"Th-The culprit left a trace."

Seeing the ominously shining eyes of the Supreme Commander, A'jandeok had trouble speaking. He barely managed to swallow his saliva before continuing.

"'I am Kangshi King… Un Yeonyeong of the Blood Cult…….'"