\chapter{The Showdown Between Humanity and Ximen Qing (8)}

There is something in the world called circumstantial evidence.

Even without any solid proof, it is a conviction that one suspects must be true from the heart.

The Blood Cult suddenly appeared?

It was such an obvious ploy that not even a child would be fooled.

But then again, it just had to be the Blood Cult.

She might have been able to scream that this vile and vicious woman was looking down on her, but since it was the Blood Cult, they really could do something like this.

The Blood Cult truly had no reason for perpetrating their Blood Sacrifices.

Wasn't it a group of people who committed such atrocities just because they were bored, because they could, or simply because they felt like it?

The Blood Cult was an evil group, infamous throughout the world, that killed and tortured people simply because the world was hateful, people were hateful, or for no other reason than that they enjoyed it.

It was clear that he was frustrated and resentful.

But he couldn't shout out and call out his enemy.

The heart of the Fort Commander, Wang Cheolgun, was crumbling.

So the Fort Commander shed tears of blood once again.

"Ugh. Commander."

"Keueuk……… Euk."

Whether it was Ximen Qing's doing or the Blood Cult's, his precious daughter, who he wouldn't mind putting in his eye, was dead.

"No, it's Ximen Qing. It has to be Ximen Qing."

Even if Ximen Qing did it, it was Ximen Qing's doing.

Even if it really was the Blood Cult, whose fault was it that the main base was empty?

Ximen Qing! It's Ximen Qing!

At this sight, A-Jeondu realized that the saying ‘shedding tears of blood' was not a metaphor.

When anger and sorrow reached their extremes, the blood vessels in the eyes burst, causing one to truly shed tears of blood.

He was so shocked that he just stood there in a solemn manner.

And he was doubly shocked to see that even these scumbags, who were utter human garbage, cherished their children.

Dou Sam had already seen tears of blood the previous time.

At first, he was outraged, but the second time, he had no particular reaction.

If this went on, wouldn't it become chronic, with blood mixing in his tears every time he cried? Then, shouldn't his moniker be changed from Jade-Eyed Ferret to something like Blood-Tears Wretch?

He had the leisure to even think of such things.

And he was actually thinking of other things as well.

In fact, Dou Sam, who had no family, did not really understand.

And to begin with, those two, who had no skills whatsoever, were just abusing their father's power to commit evil deeds, so he had already thought that they wouldn't live long on their own.

Dou Sam had only seen tears of blood twice.

Even so, the power and impact were significantly reduced.

The destructive power of anything is strongest the first time.

However, the second time, it is reduced to less than half.

But the third time, people would be so used to it that they would think, ‘Are they seriously going to do that three times in a row?' and let their guard down, thus causing the destructive power to rise again.

By the fourth time, people would just think, ‘What? Again? I'm not falling for this anymore', and have no particular reaction.

This is why one should only do something up to three times.

Starting from the fourth, one will only receive criticism.

However, people always make the same mistakes.

Once they succeed once, twice, and then three times, they become excited.

And it feels like they have learned a trick, thinking, ‘Ah, so this is how it's done'.

Qing was someone who could be called the Heavenly Maiden due to her beauty that could be argued to be the greatest in the world, her strength that transcended humans, and her realm that was far beyond her age, but in the end, Qing was also just a human.

Alright. If I do this, they'll burn even more?

Now, wouldn't it be better to completely disable these Green Forest bastards so that there will be no trouble in the future?

On the first day, Qing had burned down the main base. On the second day, she had burned down the branch base on the neighboring peak and the third base below the valley.

This was two times.

However, perhaps if it was the Blood Cult, the other bases might also be in danger. Due to A-Jeonduk's judgment, the two burned bases were discovered the next morning.

And that day, the fourth base next door and the forward logistics base below were burned down.

This was discovered on the very same day.

This marked the third time.

And so came the fourth day of arson.

It was the fourth time everyone dreaded.

Qing made another hole in the stockade with Sword Force.

What's this? There's no sign of anyone?

They couldn't stop the fire, so did they just remove everyone?

Ah shit, this isn't good.

I need to reduce the number of these bandit fuckers as much as possible. What do I do if they say, ‘Burn it all down, we're leaving'.

What do I do? I have to burn it all down, of course!

Qing could now be considered a proper arsonist, capable of burning down at least one building per day.

She had a rough idea of the structure of the base, so she quickly found the bedroom of the Base Commander.

Agh, the smell.

Seriously. These bandit fuckers need to ventilate!

Qing scrunched up her face at the smell of a bachelor that could make her nose fall off and opened the closet and the blanket chest, picking out the dirty things with her outstretched arm as if using tongs, before piling them on the bed.

This is trash that will never smell good even if you wash it.

It's not even fit for a clothing collection box; it's just burnable trash, so I should just burn it.

Then, she lit the oil lamp and knocked it over, thus concluding the arson.

This was the trick to arson that Qing had figured out.

It was difficult to set fire to a perfectly fine house.

If you gather things that burn well and start a big fire inside, at some point, it spreads throughout and burns brightly.

Thus, just as Qing was lighting the oil lamp…

"This is ridiculous."

"Gasp."

A voice was suddenly heard from behind.

Qing inhaled sharply and quickly drew her sword.

How? There was no sign of anyone?

Qing's senses transcended humans.

So if she hadn't noticed, it wasn't because she was careless, but because the other person had the ability to deceive her keen senses.

Seeing Qing already drawing her sword and aiming it at him around the time he said ‘ridi', Dou Sam, the leader of the Mount Liang, thought, ‘Oh, she's fast. Fast', and swallowed his admiration.

Not only that, but her revealed face was of such a peerless beauty that it was no lie to say she was the most beautiful woman in all of history, living up to the rumors.

Even Dou Sam, who had no interest in women, found it hard to take his eyes off her, feeling dizzy for a moment.

However, he did not show it and opened his mouth, releasing a stream of ridicule.

"For a righteous female warrior of the Orthodox Faction, you are quite vile, reaching the very heavens. And to think your methods are so cruel that even the Heavenly Slaughter would step aside. Furthermore, you dare to falsely use the name of the Blood Cult and, not only that, you're even setting fire to other people's homes."

But Qing was confident.

"I keep hearing that. How can a righteous female warrior of the Orthodox Faction do this or that. Do you think all the martial artists of the Orthodox Faction are idiots or something?"

Qing continued.

Why should the Orthodox Faction keep promises made with their enemies?

Why should they avoid cowardly methods and only boldly charge straight through the front door in broad daylight, after giving prior notice?

Torture is not allowed. Cruelty is not allowed.

And when killing, it had to be done instantly and painlessly, with mercy?

Isn't that just being an idiot, not being part of the Orthodox Faction?

"Well. Is that not so? Otherwise, why bother calling yourself the Orthodox Faction? If the Orthodox Faction acts like the Unorthodox Faction or the Blood Cult, there is no reason to call oneself Orthodox."

"Ehhh. Tactics are just tactics. The Orthodox Faction is righteous because it is righteous, and the Unorthodox Faction is just a bunch of useless garbage that is harmful to the world."

"That may be so, but are all the martial artists of the Unorthodox Faction just garbage? I highly doubt that."

"Hmmm. Maybe so, but not those of the Green Forest, right? They're just parasites that get more beneficial to the world the more you kill them."

"So you killed them cruelly just because it's okay to kill them?"

"You have to kill them cruelly. The more miserable their deaths, the more people will think, ‘Oh, how nice it is that those bandit fuckers are dead. I should never become a bandit'. That's how it works, you know?"

"Hmmm."

"I'm confident, righteous, and doing good deeds for the world. The only way these bandit fuckers can be of any use to the world is by dying as quickly as possible."

At this point, Dou Sam felt displeased.

"Do you perhaps have a grudge against bandits?"

"Not really? But if you see a bedbug or a flea, wouldn't you kill it on sight? People play with them, burning or drowning them when they're bored. Does anyone call that cruel or evil?"

There was no one like that in Zhongyuan.

However, to the east, there was a scholar named Yi Gyubo who spouted nonsense about how fleas and dogs were equally precious as living beings.

But Yi Gyubo was also the same person who proudly talked about how he demolished his servant's hut to use as firewood for his own room, saying ‘Look how great I am' all over the neighborhood.

Since servants were lowly, it was natural for them to be cold, shiver, and feel miserable. However, since scholars were noble, it was only right for them to warm themselves in hot rooms and live by exploiting others. That was just how great and enlightened he was.

Therefore, Yi Gyubo's ‘On Loving Living Things' was closer to being a pretense to satisfy his own intellectual vanity than an advanced ideology that discussed the value of life.

In fact, given that he referred to himself as Ija and elevated himself to the same level as Confucius and Mencius, it wasn't hard to see his true colors.

With the world's perception being what it was, how could a lowly bandit possibly respond to Qing's words?

However, it made the bandits listening feel quite bad.

So, he tried to refute her.

"It sounds like you're saying you pass judgment on who is a bedbug and who is a flea."

"Do I really need to pass judgment? Then, can you tell me just one way the Green Forest is beneficial to the world?"

"That is."

Dou Sam's words were cut off.

What good could a bandit possibly do for the world?

"See? Even a three-year-old child knows that the Green Forest bastards are useless garbage. Isn't cleaning them up the duty of a righteous warrior of the Orthodox Faction?"

Hearing that made him feel a sense of shame.

For a master of the Unrestrained Realm, it was possible to enjoy wealth and honor anywhere in the world as a master among masters.

Wasn't the reason he was toiling in this remote mountain, only to hear insults from a girl the age of his daughter, all because he was a bandit?

It was all Dou Sam's fault for starting a verbal spar with Qing in the first place.

"Ahem. Anyway, I have a suggestion for you. If you do me a small favor, you can leave this place alive."

"What is it?"

"Bear my child."

This time, it was Qing who was at a loss for words.

What? Is he insane?

"After hearing what you said, I understand. I will raise my son to be a proper person, not a bandit, so don't worry too much."

Our son? Qing was utterly disgusted.

"Wh-What the hell are you talking about all of a sudden?"

"You are at the Transcendent Realm at such a young age. If my son inherits even half of that talent, wouldn't he be born as a martial genius?"

"What about my opinion?"

"If you want to live, you'll have to give birth. I know you're pretending to be fine, but you're already exhausted and your stamina is depleted. For your information, I have reached the Unrestrained Realm, so even in your best condition, you wouldn't stand a chance."

"Hmm. Fighting is a bit much and I was thinking of running away. I'm confident in my ability to escape."

"The elites of the Green Forest are already spread out outside. If the signal flare goes off, even the Fort Commander will come. Can you escape the two of us, both Unrestrained Realm Masters? Can you?"

Qing broke out in a cold sweat at that.

Ah shit. This seems like a big problem.

"Elder Brother? As you ordered, the Net of Heaven and Eart- Keureuk."

One of the Mount Liang members came to report to Dou Sam, but suddenly grabbed his neck and collapsed.

Qing was startled.

Previously, the old man from the Imperial Palace had said that due to the aftereffects of his technique, his body was slow.

And since the old man was constantly low on Inner Qi, he could only use Force Compression once, so he was only looking for an opportunity from afar.

Thus, this was the first time she had seen a true Unrestrained Realm Master's proper speed, and the speed of tearing out someone's Adam's apple was truly terrifying, to the extent that it was instantaneous even to Qing's keen eyes.

I thought that since I surpassed the Transcendent Realm, I could stand a chance against one Unrestrained Realm Master.

But it seems they're faster than I thought.

Qing's expression hardened.

At this, Dou Sam was triumphant.

"Now. Do you see? I'm serious. Serious enough to kill my own subordinate. If you agree to bear my child, I'll let you go. Just give birth to a handsome son and you can leave. I'll even breastfeed the child myself if that's what it takes. I won't make you do it. So, you can leave as soon as you give birth or after you recover, whatever you prefer."

Qing started to think.

Running away and setting fires, killing bandits, setting traps, and if an opportunity presented itself, taking on one at a time was the plan.

But what if…

If she tried to create a child, she would be defenseless.

Wouldn't it be possible to take out one of them with a single strike of Buddha's Palm? 