\chapter{The Showdown Between Humanity and Ximen Qing (14)}

In a clash between experts, especially when facing an opponent superior to oneself, turning one's back could prove fatal.

However, since the opponent also turns their back, it could be considered fair in a way.

Why do they always have to appear with their backs turned, though?

As soon as she appeared, Qing quickly turned her body.

The bandit leader, despite his title, was faster than Qing, as if he was a master of the Unrestrained Realm.

Wang Cheolgun had already taken a step towards Qing.

This was a significant difference.

For a martial artist, a single step involves kicking off the ground with a powerful force.

With three steps, one could reach nearly their maximum speed, so the actual distance was already reduced by more than half.

This is why Qing hated the Ethereal Steps.

If only she had charged forward instead of turning her body upon appearing, it might have been a surprise attack where she rushed in with her back to the enemy. However, in this kind of confrontation, it was like giving up a move after evading.

Qing gritted her teeth and drew out her Sword Force.

In Wang Cheolgun's hands were hammers, spiked clubs.

A spiked club was a weapon with a lump of iron attached to the end of a club.

Usually, it had a mace head with sharp spikes, but this one had hammerheads instead.

But still, doesn't a spiky iron ball have more destructive power than a hammerhead, no matter how you look at it?

Was it some kind of unique weapon with a special technique?

It was a weapon Wang Cheolgun made to capture Qing alive.

Being struck by a flat, broad hammerhead wouldn't result in a fatal wound like a spiked mace, but rather broken and crushed bones.

Wang Cheolgun's hatred, promising to make her regret being alive, was genuine.

Three steps. Wang Cheolgun raised both arms high.

Although he had blades stuck in his forearms, the pain didn't reach his enraged mind.

The hammerheads were hidden behind Wang Cheolgun's back.

To Qing's eyes, only his raised hands and elbows were visible, with his forearms hidden behind him.

In Qing's mind, thousands of Ximen Qings swung their swords.

Imaginary futures, yet all of them were gruesome.

Hammerheads slammed down, cracking skulls. Another Qing had her arm struck, her own elbow smashing into her torso, shattering ribs.

One Qing was hit in the stomach and sent flying, another had a shoulder struck, resulting in a separated lower arm.

This was the vision of an Emperor, where a single gesture or step brought about changes throughout the entire world.

However, among the myriad of Ximen Qings, a few…

There was one Qing who deflected the hammerhead with an obliquely raised sword.

Another Qing's sword slid along the shaft of the spiked club, targeting Wang Cheolgun's hand-

Yes, let's go with that sword.

Accordingly, Qing assumed the posture of the imagined future.

Infinite calculations unfolded in the moment Wang Cheolgun took his second, third, and fourth steps.

This was the sword of the laziest, yet most dominant Emperor in the world.

Five steps. Qing's eyes flashed.

Just one more step!

However, Wang Cheolgun was an expert of the Unrestrained Realm.

Stopping on the fifth step, the arms hidden behind him extended forward, carrying the momentum.

The right hand. It was his right hand.

His right hand gripped the very end of the spiked club, swinging it one-handed from seven feet away.

If I dodge… No, it's too late. Damn it.

Qing abandoned the prepared sword trajectory and raised her hand to the blade.

With a fierce push of True Qi, the Moonlight Sword hummed as if it would shatter.

It's fine. If I can just deflect the hammer upwards and create an opening-

But in that instant, the hidden left hand suddenly grabbed the spiked club and twisted its trajectory.

It struck the sword at a right angle. Clang!

Wang Cheolgun intended to break the sword.

However, Qing's Sword Force, though not fully compressed, was not lacking in sheer quantity.

Moreover, it was a greatsword with a blade twice as thick to add weight.

Even after being struck by the hammer, it held firm.

But the impact still came through.

Qing's body was not an ordinary one, so the impact was transferred to the ground. However, the ground she stood on was just an ordinary gravel field.

With a crunch, Qing's stepping foot sank into the gravel, sliding three inches.

For a moment, her body's center swayed, causing her to stumble.

At that, Wang Cheolgun took another step, his other foot sweeping low to the ground, aiming for Qing's ankle. Smack!

"Oof."

However, the sound that escaped Qing's lips was not a scream, but a gasp of surprise.

Because Qing's ankles were incredibly strong.

It wasn't literal, but her body's durability, transcending that of a human, made her bones stronger than steel.

Moreover, with the addition of the self-defense mechanism ingrained in her body from the countless naked training sessions in the Divine Maiden Sect, Qing's bones were even sturdier than her muscles.

Pain surged, but that was it.

Instead, the problem was the sudden loss of balance, with both feet floating due to the slippery gravel and the world tilting sideways.

A martial artist's strength usually came from the ground.

In such a floating state, it was difficult to exert proper force.

Ah. Something big is coming.

The senses of the Awakening Spirit Skill painted a vivid picture of her surroundings.

The left foot of Wang Cheolgun, kicking her ankle and stepping on the ground, followed by the rising right foot, the knee.

Where? Towards my side.

In that brief moment, Qing extended her left arm.

And. Thud!!

Her breath was knocked out of her.

The world spun wildly.

Qing, kicked, flew like a thrown stone, bouncing twice on the rocky ground before rolling.

"Argh!!"

A scream erupted.

But it wasn't Qing's.

Wang Cheolgun screamed, clutching his forearm.

Qing, who had been rolling, quickly got up.

In her left hand, she now held a viciously barbed dagger.

Judging by the flesh clinging to the hook-like blade, it was clear it had been embedded in someone.

When floating in the air, without ground to stand on, even a forceful attack lacks power.

However, the advantage was that even if struck, the impact was converted into momentum, reducing the strain on the body.

Therefore, enduring a hit, Qing had reached out to Wang Cheolgun's forearm and grasped the handle.

Looking at Wang Cheolgun's gaze, a mix of hatred and pain, Qing taunted him.

"Why are you looking at me like that? Wow, I'm so hurt. I didn't pull it out, you know? I just happened to grab what was in my hand and you kicked me. It's like having a tooth pulled. Do people in Zhongyuan tie a string to it and kick it out?"

"I'll kill you!"

Wang Cheolgun charged again.

Qing had learned from the one hit.

Depending on where he gripped the long club, he could freely adjust the distance, could he not?

She thought it would be easy to read the trajectory since it was a two-handed weapon.

He also used it with his left, right, and even just one hand.

Depending on where he gripped it, the hammerhead moved so freely that it was even more difficult to deal with than the swords she was familiar with.

If she tried to block or deflect based on his posture alone, she'd be in for a nasty surprise.

Taking a bruise on the side and learning that was a cheap lesson.

Wang Cheolgun charged.

Instead of a clumsy counterattack, Qing chased him with her eyes until the last moment. She took one step to the right, one step back, and quickly leaned her body to the left, dodging the spiked club.

Wang Cheolgun's hammerhead vertically split the air, passing right in front of Qing's chest.

Opportunity!

It was the moment Qing's eyes lit up.

CRASH!!! The hammerhead slammed into the ground, overturning the earth.

Instead of resisting the force pushing her body, Qing rolled back gracefully, using her hands and feet to create distance.

Damn it, if I block, I stagger. If I don't, I'm sent flying!

What a dirty bastard!

Wang Cheolgun was furious.

"You rat-like bitch!"

"I'm a rat? Then did your children die to a rat? Squeak! Your children, squeak! They're in hell, squeak! Serves you right, squeak!"

"I'll kill you! I'll kill you!"

Wang Cheolgun's eyes had lost all traces of white.

They were completely bloodshot, not just with visible veins, but from the blood vessels bursting.

The inside was black and the outside red.

The furious hammering, fueled by his rage, was powerful and faster, but it also made it easier for Qing to see where he was aiming.

"Squeak! The rat can't even catch an old man, squeak!"

"Kaaaaaaaah!"

"Daddy! Cheer up! We're not here! Son! Not here! Daughter! Not here!"

"Uwaaaaaah!!"

Qing completely gave up on her sword and was now fully committed to running away.

Because she had something to believe in.

Isn't applying poison to a dagger just common sense?

She had rummaged through Yangsanbak and found a bunch of suspicious medicine bottles instead of secret manuals or treasures.

She had even mixed in some herbs to make it more potent.

Now, his blood was boiling, and his rage was through the roof, so he probably didn't even notice the poison spreading through his body. However, if he calmed down a bit, he might try to escape and expel the poison.

That was why Qing was constantly provoking him.

Honestly, bringing up his dead children was a bit, just a liiiiittle, pitiful.

But it's not like we can live under the same sky, right?

But was the poison's effect too weak?

Shouldn't it be time for him to collapse, spitting blood?

His tongue felt numb. Was it not poison but some secret spicy seasoning?

Qing was bewildered by Wang Cheolgun, who was still full of vigor.

But time was on her side.

"Hey, old man. Your children… Ugh, let me talk. People should be able to!"

"Die!"

"You keep saying die! I don't want to, okay? You die! Potatoes are delicious in spring! Your house doesn't even have children, right?"

"Kaaaaaaaah!"

Over fifty exchanges had already passed, yet the bandit leader showed no signs of collapsing.

Whoosh, the hammerhead brushed past her head.

Whooosh, the hammerhead brushed past her shoulder.

Whooooosh! Whoosh! Whoooosh!

But the speed was noticeably slower, and without any feints, the attacks were becoming simpler, making it much easier for Qing to dodge.

The hammerhead that had just grazed Qing's nose spun widely behind her. Is he going to swing, thrust, or raise it high to strike down?

It was the moment Qing was concentrating on reading the ever-changing movements of the spiked club.

Suddenly, within the range of her Awakening Spirit Skill's senses, from three directions behind her, an ambush!

Why! Why from behind!?

She had been fighting with her back to the forest, just in case arrows might be shot from across the river.

But suddenly, attacks from behind? Ah, this.

A little while ago.

Sanroe A-Jandeok lowered his voice.

"Hey, Heavenly Slaughter."

Yangsanbak's 22nd rank, Heavenly Slaughter, looked at Sanroe.

"Take the brothers and help the Chief. She seems to be barely dodging, but if you create just a small opening, wouldn't that be enough?"

"If we intervene, we'll die, Senior Brother Sanroe. And we might end up hindering the Chief instead."

"Still, if we have numbers, even if we hinder him a bit, we'll eventually win, won't we? Can you see the situation right now? If the Chief wins like this, our Green Forest will be halved.

"There's no need for those who would flee anyway."

"You fool. Is this just about killing that bitch right now? If one of the two Unrestrained Realm experts dies and our numbers are halved, do you think the Orthodox Faction martial artists will just stand by? It'll give them a pretext. If a massive purge begins, where in the world can we hide? We need to at least capture her and then persuade the Chief to let her go, maybe cripple her, and negotiate. That's the only way for the Green Forest to survive."

"That's… Eigh, damn it."

"You know the Chief's promise, right? If we capture Ximen Qing with merit, you know, right?"

"Hah. Right. If you die once, why would you live twice? I should set up my own stronghold and become independent. The hell with the title Heavenly Slaughter. Even if it's Yangsanbak, why such a garbage title for a star."

And so, now.

Thump! A sharp pain struck her back.

A significant amount of True Qi was depleted.

It was a palm strike infused with considerable True Qi.

But being pushed forward was more problematic.

The hammer was closing in on her temple!

Qing covered her head with both arms, thinking, Ah shit, I'm screwed-

"Ugh."

Wang Cheolgun's spiked club bent downwards.

The hammerhead slammed into Qing's side.

Thud, nearly half a foot deep.

"Gasp."

The air in her lungs was forcibly expelled as her torso physically shrank in volume.

It was a blunt weapon enhanced with the mysterious power of Qi.

Struck by it, Qing was thrown like a stone, bouncing twice on the ground before plunging, splash!

Into the late autumn's icy river water!

Qing's mind cleared instantly.

The pain was excruciating.

But her mind was more vivid than ever.

In Qing's hometown, it was said that this was due to endorphins in the brain during a crisis, but Qing, being uneducated in such matters, didn't know the specifics.

However, she knew that running away now would be suicide.

Qing grabbed a rock at the bottom of the river and held her breath in the dark water.

She opened her mouth and rinsed out the blood that filled it.

Damn, I can't breathe. I'm going to die.

She had lost all her breath when she was hit.

If she had taken a deep breath, she could have lasted for at least a quarter of an hour, but not now.

What to do? What should I do?

How can I beat a crazed Unrestrained Realm expert and a bunch of others who are ready to hinder me?

These dirty bandit bastards ambushed me?

How can they be so underhanded as to ambush a person?

Vicious bastards who ambush people should have their limbs torn off.

At this, one might ask if Qing wasn't the foremost candidate for dismemberment.

But Qing had never ambushed a person, only those who were not human but merely resembled humans, so she was innocent and blameless.