\chapter{The Showdown Between Humanity and Ximen Qing (6)}

After the first offense, Qing realized that these bandits didn't care at all about those left behind.

Come to think of it, wasn't that guy from the 37th squad of Yeonam's Stronghold, Daecheol, who had donated the upper garment she was currently wearing, also appeared alone?

If you're going to fall behind, then fall behind.

If you don't want to fall behind, then keep up on your own.

Normally, when doing group projects like this, shouldn't you take care of the one who falls behind the most?

Qing briefly recalled group projects during her college days and thought, ‘Hmm. Come to think of it, it seems like it was right to just abandon those who fell behind.

I should have removed the names of seniors who didn't do anything from the presentation. Yeah. What loyalty.'

Thus, Qing's job of twisting the necks of the bandits became very easy.

Since the bridal wreath was blooming and no one was looking back, all she had to do was approach and bonk!

A miraculous reunion of the back of the head and the spine!

Only a few, very, very special people in all of humanity could have such a precious experience, and those who did were so moved and touched that they lost their will and collapsed, becoming nothing more than corpses.

As one by one took the journey to the afterlife from the back, only two were left.

Bark, bark! Bark!

Then, a dog barked from the front.

At that, a rustling sound was heard as the dog handler emerged from the bushes and spoke discreetly.

"Shh, Boss, I think I found them."

"Really? First, the one with the net."

"……"

"What, the one with the net. Aren't you going to answer?"

Cheonam frowned and turned his head.

And there was no one there.

Cheonam was dumbfounded.

These bastards are so undisciplined.

He hadn't moved that fast, but everyone was left behind?

It was then.

A rustling sound of someone stepping on leaves was heard, gradually approaching. Finally, the staggering figure of a person narrowed the distance from the hazy other side.

"These, damn. Even a cripple is catching up. Hey. Did you see the others?"

"T-That, Boss, that's, that, I, I di-didn't see anyooooone."

As he heard that, Cheonam thought.

This bastard is going to get into big trouble if I ever have him lie.

"Aren't you going to speak properly? Which stronghold are you from? I'm going to gather everyone from your superiors to my subordinates? You're all so undisciplined. How dare you try to scam a Senior of the Yangsan Marshals?"

"Oh no. That's, cough, they all said they were too tired and wanted to rest before coming."

"These sons of bitches. Does it look like I'm fucking around because I want to? Where are they?"

"That's, ckhhk, cough, cough! There."

"What? Where?"

"Boss, uh, my position is a bit."

"What, you bastard? Are you saying you want me to take care of your position now? Is this bastard crazy? Put your head down."

"Boss, I'm a patient……"

"What do you mean, a patient? This bastard."

Frowning deeply, Cheonam strode forward and raised his arm.

And then, just as he tried to slap the guy's cheek as he always did, the guy impudently grabbed his hand and blocked him.

"Oh, you blocked it?"

"Then should I not block it? I'll send you to the afterlife too, so you can rest. I'll send your boss and your brothers all together."

The sudden beautiful voice made Cheonam momentarily dumbfounded.

But in front of an enemy, being dumbfounded could lead to big trouble.

Cheonam's grabbed arm folded in half with a snap.

"Cough."

The air in his lungs automatically turned into a scream and tried to escape, but his windpipe was blocked, so the air just gave up and returned to his lungs.

Qing, who had grabbed Cheonam's neck, smiled.

"Sorry to tell you in advance, but the cripple is the culprit and the bald guy is a ghost."

Then, Qing lifted Cheonam with one hand and pushed him with momentum.

A branch protruded from Cheonam's solar plexus.

After Qing let go of him, Cheonam was left hanging on a thick, low branch of a large tree.

The aim might have been a little off, so it didn't pierce his heart, but he was skewered either way, so he wouldn't live long.

"Boss? Are you there?"

"Ah. There was one more."

After impaling Cheonam on the tree, Qing turned around.

Even as he was dying, Cheonam couldn't understand.

He could understand that the cripple was the culprit.

But why was the bald guy a ghost?

However, soon after, Cheonam's breath stopped, so he could not understand until his death.

Qing was a judge who sentenced the death penalty after looking at Evil Karma, so there were no misjudgments.

After Ximen Qing punished the dog handler with the same sentence, she disappeared into the forest.

Thus, there was no one left.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing diligently hunted down the bandits.

It was something she truly desired from the bottom of her heart, but even if it wasn't, she had no other choice.

Thus, Qing continued to clean up the trash of the greenforest bandits, thinking to herself, ‘You fucking bandits. How dare you throw trash in the forest so thoughtlessly?'

Qing, dressed in the clothes of the bandits, was invincible.

This was because it was one of the most vile war crimes in the world.

Originally, in war, disguising oneself as a civilian or looting and wearing the enemy's uniform was a violation of international law.

But now, there wasn't even a single international organization in this primitive era, so it could be said that it wasn't a big problem.

And so, how many had she killed?

Finally, a mountain slope that could be called a mountain, rather than a cliff, appeared.

Finally! This damn jungle is finally over!

Of course, in Qing's standards, it was a mountain slope.

In an ordinary person's standards, it was just a cliff made of dirt and trees instead of bedrock.

She could escape by climbing the mountain like this.

But she couldn't.

She had already become irreconcilable enemies with these bandits, and look at how many people were mobilized, not even considering the two Unrestrained Realm Masters.

Even if they were mixed with Third and Second-Rate, over 500 troops were mobilized this quickly.

If she didn't break their momentum here, they would become a persistent nuisance.

Perhaps it would not only affect Qing but also harm those around her. In fact, this was the most crucial matter.

It's not just me, but also that guy, Gunyeong1.

Even if it wasn't Gunyeong, she was staying in Nakseong and had gotten along well with the Great Clarity Commerce, so they might vent their anger there. She couldn't be certain they wouldn't touch the Divine Maiden Sect.

After all, ignorant people often did things without thinking and regretted it only after the fact. So if bandits just went ahead and did something without thinking about the consequences, causing acquaintances or acquaintances of acquaintances to bleed, it would be a regretful and tweety matter for a long time.

If I had known this would happen, I would have killed all those bastards when that Young Master died… No, wait, there were so many of them. It would have been difficult from the beginning.

Yeah, like in the Black Storehouse, I should have shouted out that I am Un Yeonyoung of Jinju in Hebei Province.

Qing regretted belatedly.

She completely forgot about the thoughts she had until just now. It was clear that the attitude of someone who thought that ignorant people often did things without thinking and regretted it only after the fact should absolutely not be as such.

So the reason Qing searched for the mountain slope was not to escape.

She heard that there were eight strongholds around here, so she thought she should destroy at least half of them.

Thus, Qing climbed up and up the mountain slope.

It was a little steeper than the steep hill she had descended from Yukrak Peak. It was easier to go up than down, however.

It was easy to dig her hands and feet into the dirt wall, and the densely growing trees had roots that supported the dirt cliff, so she could jump while holding onto the trees and stepping on them, diligently making her way up.

Then, around the 70\% mark of the ridge, a thick fog set in, limiting visibility to about three zhang3.

This wasn't unusual.

The climate of the Zhangjiajie region was such that fog often formed in the highlands, with fog present for 250 days out of the year.

As the bedrock appeared with the fog, Qing circled around it and found a fortress hidden behind the peak.

Hmm. But…

I don't know which mountain this is or which stronghold this belongs to.

Well, do I really need to know?

After all, there would only be bandits in a stronghold.

There were only bandits in a stronghold.

Because, as much as bandits were human, they couldn't live on such a steep mountain.

Even if they managed to steal a lot of gold and silver through robbery, it didn't mean that water, grains, and cooked food would be plentifully available every meal.

So for bandits to live in large numbers on a mountain, they had to carry food and other supplies every day or every few days.

It was a very inefficient and difficult method.

So how?

The bandits also set up villages at the foot of the mountain to live in.

Moreover, since bandits also had families, they needed villages to live in at the foot of the mountain.

Therefore, villages attached to remote places without proper roads were either fortified villages or bandit villages.

It was rare for a fortified village to accept outsiders, and even if they did, they would be watched with all kinds of wary gazes.

However, if there were such villages that welcomed outsiders and even served meals, nine out of ten were bandit lairs, so one should flee immediately.

Thus, a stronghold of the bandits was not a home to live in, but a workplace where they took turns staying.

There were only employees at a bandit's workplace, so in other words, it was okay to just behead everyone she met.

Qing reached the fortress wall and looked up.

Due to the fog, its height was not visible, but it was a magnificent barrier built with huge trees that were at least ten zhang tall.

The bandit bastards really do take care of their own safety, huh?

However, what meaning did a wooden barrier have in front of a Transcendent Realm Master?

After neatly cutting out a square with Sword Threads, a doggy door was created in less than a moment.

In other words, Qing had infiltrated a stronghold where all the main forces had left, leaving behind only the dregs.

In technical terms, this act was also called a backdoor or a base snipe.

Thus, Qing was on a rampage.

No one could stop her.

Qing was a Heavenly Slaughterer.

Those remaining in the stronghold were individuals more skilled in facility management than combat.

Qing had mastered a stealth technique called the Black Shadow Stealth and moved without making a sound through her practice of the Divine Footsteps.

Even if someone saw Qing, the scene would feel so out of place that they would wonder if they were seeing a person or a ghost.

Moreover, with the thick fog, no one could even spot Qing until it was too late.

Thus, Qing was roaming the stronghold, accumulating Righteous Karma, when…

She saw smoke billowing from a detached building.

As Qing approached, she saw white steam rising from a head-sized window about two zhang above the ground.

Uh. Perhaps. This is it?

Silently, Qing jumped up, hooked her fingers on the window, bent her arms, and peered inside.

Her face was immediately hit with hot steam.

And the sound of splashing water.

There was already someone here, but from the back, it seemed to be a woman? A female bandit? Come to think of it, have I ever seen a female bandit before? Well, I guess women can be bandits too.

Her Evil Karma indicated she was a skilled bandit.

But more than that, a bath! It's a bath!

Qing's eyes lit up.

Soaking in a hot bath, letting the heat seep into her body, was one of Qing's favorite things to do.

It was a luxury only available in the high-end inns of large cities, and it was quite expensive due to the cost of firewood and the labor to transport and boil the water. However, it was one of the few luxuries Qing enjoyed, along with food.

She was already damp and sticky, so a hot bath would feel amazing.

Just as a sparrow cannot pass by a mill, Qing could not pass by a bath.

With her eyes gleaming with desire, Qing circled around the building's wall.

There was one guy guarding the entrance.

If you could call it guarding.

He was sitting against the wall, with an axe stuck into the ground. His hands were folded on top of the axe handle, and his forehead rested on his hands as he slept soundly with a ‘Kooool'.

There was a certain poignant weariness in his posture, but after all, if a bad guy was weary, it must be because he was doing bad things, right?

Sleeping outside like this, he might catch a cold.

So Qing twisted his neck for him.

Having received such a great lesson that one could die if they slept outside without any preparation, he would not be so resentful on his way to the afterlife.

Thus, Qing carefully opened the bathhouse door, and seeing no one else inside, she peeked further in past the changing room.

How many guests are there? Just one, huh.

It was a well-made bathhouse for a bandit's lair.

First, she headed to the side door in the corner, where she saw firewood half-burned in the furnace.

Qing took the firewood stacked next to it and shoved it in, greatly increasing the firepower.

With this, my bath preparations are complete.