\chapter{The Showdown Between Humanity and Ximen Qing (5)}

Even dogs are quick-witted creatures.

The hunting dogs that had accompanied Qing remembered her scent.

However, they also read the hostility of the masters who were looking for Qing. As such, they simply decided to trot around casually after recalling the affectionate touch that used to caress them.

Thus, the hunting dog that found Qing was one that had never met her before.

But Qing was not.

Bark! Bark!

-This way! Ximen Qing is over here!

"No, wait, Blackie! Is it okay to betray me like this? But wait, are you Blackie, Black, or Black Three?"

However, the hunting dog that had never seen Qing before merely bared its teeth, threatening her fiercely.

At this, Qing tilted her head.

Hm, I guess it's not a dog I know?

"Are they Blackie's siblings?"

Of course, Blackie, Black, and Black Three weren't actual siblings.

Grrrrr, bark! Bark!

"Hey. Shush. Can't you be quiet?"

Hiding in a tree and gnawing on a pheasant, Qing frowned and rebuked the dog.

"They say not to bother a dog when it's eating, but what the hell. You're really bothering me. Hmm. Did I overcook this a bit?"

Qing chewed on the pheasant breast.

Pheasant meat was a bit tough, after all.

In fact, Qing was far too relaxed.

Although Ah Zandeok's terrifying scheme had not gone according to plan in the slightest, it did have one accomplishment.

The scouting party sent to find Qing were the lowest of the low, the scum of the scum.

As such, Qing couldn't help but think that the skill level of the bandits of the Green Forest was utterly pathetic.

And that was why she could be prevented from escaping until now.

She didn't think hundreds of these guys would be much of a threat, so Qing remained relaxed.

That's why she was still just continuing her meal, even at a time like this.

Thus, the encounter with the Green Forest pursuit team!

A bandit pointed up at the tree and shouted.

"Ximen Qing! It's Ximen Qing! Right th-!"

Crack! The bandit who was about to say something clutched his forehead and crumpled to the ground.

Qing smacked her lips.

She had tried flicking an unknown tree nut, but as expected, it was too small and light to have any power as a projectile.

It would have been nice if she could crack people's heads with these, but it was a shame that it didn't work out that way.

Qing thought as she tore off the pheasant's neck.

It was late autumn, so it had a lot of fat stored up for winter.

In fact, because the pheasant neck was cold, oil kept oozing out each time she chewed. Mmm, how tasty. Delicious.

"Ximen Qing! You were here!"

"Support, request support!"

Piiiiip!

Bark! Bark! Grrrrr, bark!

Meanwhile, the situation below was chaotic.

True to their name as a semi-jungle, the trees of Won Family Estate were unusually tall.

So even after finding Qing leisurely sprawled on a thick branch dozens of meters above, there was nothing they could do but stomp their feet in frustration.

"Cowardly bitch! Can't you come down immediately!"

"Ximen Qing! Come down obediently!"

"Really? Should I go down? Are you confident?"

At this, Qing responded nonchalantly.

Of course, the leader who had been shouting for her to come down suddenly thought, ‘Hmm? Can we win if she comes down?'

Until now, he had just been shouting because he was angry that she was neither showing her face nor listening to him.

But hadn't he heard that she was a terrible woman who devoured people in the jungle?

And then, he heard a beautiful voice in his ear.

"That's right. If you've eaten, you should exercise. Shall we play a bit, then?"

The leader was terrified.

If they could stall for time until the Masters arrived, their contribution would be set in stone.

There was no need to take any risks, so why would he?

"No! Don't come down!"

"You told me to come down just a moment ago, though?"

"I'm warning you! Don't come down! If you come down… Uh, um. If you come down…"

"If I come down, what? What are you going to do?"

"Uh? If you come down? That's a bit… troublesome."

"Ah. You find it troublesome."

Qing couldn't continue her words.

What is this? Is he a bit slow or something?

Well, why would an intelligent person be a bandit, anyway?

Qing accepted this and suddenly changed the subject.

"I'm full."

"……?"

"But my Moonlight Sword is famished!"

With that, Qing leaped down with a whoosh, and the yellow sunset drew a thick vertical line as long as the sword's length as it fell.

"Eek!"

Sword Force fell towards him.

The bandit froze.

He couldn't even think of dodging, just screaming and covering his face.

And then… Thud!

"Aaaagh! Aaagh! Hm?"

The screaming bandit carefully lowered his arms.

It's strange. The sword was definitely falling. Did I see wrong?

Qing was also a bit flustered.

She hadn't realized that objects were closer than they appeared when looking down from a tree.

She had leaped down while emitting Sword Force, but ended up landing behind the bandit, splitting the empty air.

Embarrassed, Qing shouted for no reason.

"An opening!"

The blade that entered from the side exited from the side.

As the bandit's upper body fell with a thud, another bandit, frozen in place with a whistle in his mouth, came into Qing's view.

"I told you it's noisy, so don't blow the whistle. I was trying to eat in peace, but you kept making all that noise."

"Hieeek!"

The leader, who had witnessed his comrade being split in half, turned around and fled in terror.

Qing stomped on the ground and chased after him with one step, two steps, three steps, catching up and slashing diagonally with her sword.

She missed!

As the bandit's figure suddenly dropped to the ground, Qing's sword once again cut through the empty air.

He had tripped over a vine set by some wicked person, a stroke of luck.

"Aaaagh! Aaaaaagh!"

However, the ground was covered in stakes.

The bandit screamed as he was impaled on stakes all over.

If he had been cut in half by a single strike, he would have avoided such pain. As such, one could say that he was rather unlucky instead.

Qing looked down at the scene.

Since it's a trap I set, though…

This low-level bandit couldn't have avoided the attack of this Transcendent, Transcendence-Transcending, Transcendence-Transcending-Qing, right?

Qing swallowed the ugly excuse.

"S-Spare, spare me……"

Those on the brink of death usually said something like this.

Especially those who valued their own lives, because they would have something to ask for before dying.

"Spare you?"

"Please. Keheok."

"Then tell me everything you know. I'll think about it after I listen."

----

Well, it turned out that a bandit barely scraping by at the level of sensing Inner Qi didn't know much.

Qing was utterly shocked by this.

Wow! You're barely at the level of sensing Inner Qi? Aren't you embarrassed to call yourself that?

What's the difference between that and proudly saying ‘I've just started on the Thousand Character Classic' after being asked if you've studied?

At any rate, this bandit, who had apparently mastered the Great Strength Tyrant Mad God Arts, didn't know much.

For reference, if one paid attention to the names of the bandit's martial arts, one would be the loser in this situation.

It was a collection of cool and powerful words, but in reality, they were just slightly improved versions of third-rate martial arts that could be found in the marketplace. As such, they were miscellaneous martial arts that were above third-rate but below second-rate.

It didn't take long for Qing to conclude that there was no way such a guy could have mastered a Divine Art.

Anyway, there wasn't much to be heard since he died on his own before Qing could spare or kill him.

But it was enough to make Qing's mind flash.

There were over 500 bandits from eleven strongholds gathered here?

Only then did Qing realize how complacent she had been.

The entire northeastern mountain range was a large mountain called Mount Cheonja, and there were eight strongholds along the mountain range surrounding Won Family Estate.

Since she had already made enemies with the Green Forest, they had swarmed out like bees from a hive once she set foot in their front yard.

Most importantly…

The Grand Chieftain of the Green Forest, Wang Cheolgun. Unrestrained Realm.

The Great Chieftain of Mount Liang, Sura Mad Warrior, Do Woosam. Unrestrained Realm.

There were two Unrestrained Realm Masters leading a group of fucking mountain bandits?

The smile disappeared from Qing's face.

This isn't good.

How should I, um, well, it would be best to escape.

But how?

Qing was someone who easily picked up on things, and such people were usually quick-witted.

It was just that Qing didn't use her brain much, or rather, she really didn't and found it annoying to do so.

Especially since acquiring a body that transcended human limitations, she realized there was no need to use her brain if her body was strong.

Her long-unused brain spun rapidly.

First, Qing took off the Divine Maiden Sect uniform, which had tracking scent well smeared on it, and buried it after folding it neatly.

Um. Master. I'm sorry. I'll try to find it later if possible.

She then tightened the straps of her chest binder and took off the perforated tops of the bandit and the half-bandit, putting them on.

The pants were just as dirty, whether it was Qing's or the bandits'.

However, it was incredibly unpleasant!

She didn't care about the bloodstains, but ah, seriously, this smell. When did they even wash these?

It was already starting to itch, and she felt terrible.

After taking out cotton cloth from her bag and roughly wiping her hands and face, smearing dirt on them, she wrapped it around her face and head.

After adjusting the straps so that the Moonlight Sword couldn't be seen from the front and grabbing a hatchet, a bandit was born, albeit one with unusually deep and pretty eyes.

As Qing was about to turn around, she paused, thinking of something.

Then she tore off a piece of the bandit's pants and soaked it in blood before wrapping it around her foot.

The 17th in command of the Mount Liang Brigade.

The Mount Liang Brigade respected the heroes of Mount Liang and dared to name themselves after the 108 Stars.

If the heroes of Mount Liang knew, they would be furious that these bandits, who had no sense of honor or righteousness, dared to use their names.

The 17th in command of the 19th Pursuit Team, Cheonam, encountered a straggler from another Pursuit Team.

"Hey, you there, which group do you belong to?"

"Keheum, I'm Yeon Angae Daecheol of the 37th group."

A hoarse voice came out.

It was an incredibly suspicious voice.

"Why is your voice like that? And why is your face covered?"

"I caught a bit of a cold. Cough. Kehehek, cough. If, if it's a bother…"

As she brought her hand to her face, Cheonam waved his hand.

"Fine. It's nothing. Don't want to catch it. The blood, did you get hurt?"

"A trap, a trap."

"Fuck, those damn traps. That fucking bitch set them up so shittily. Where are the other members of your group?"

"That, well, I don't know. I, I fell into a pit……."

It was better to say you didn't know in this situation.

If she made something up clumsily, it would only raise suspicion.

Meanwhile, a hunting dog sniffed at Qing, baring its teeth.

There was a faint smell of Tracking Incense, but since the masters hadn't given the command to ‘bite!', it was just being wary.

"Let's regroup for now."

"Thank you. B-But, Senior, my foot."

"Do I have to accommodate the likes of you? Follow as best as you can. I won't look for you if you fall behind."

"Ye-Yes, alri, cough, alright."

Cheonam clicked his tongue at Qing, who coughed as if she would vomit blood.

Her limping was severe, as if she had badly injured her foot from the blood-soaked foot wrap.

If Qing had seen such a straggler, she would never have allowed them to join.

After all, a limping person was a characteristic of traitors and serial killers.

However, the primitive and uncivilized people of ancient China had not yet developed such common sense based on scientific facts.

Thus, the search began again.

Since the dog handler was clearly urging the hunting dogs to find Ximen Qing while standing right behind her, the dogs didn't know what to do but followed the scent.

The search party following behind also moved forward, holding their weapons forward to avoid the ankle ropes and making loud noises by sweeping the leaves with their feet. As a result, they moved through the forest at a rather slow pace.

She followed closely behind the very last one.

Then, with a movement that seemed to bounce from the tip of her toes, yet made no sound even when digging deep into the leaves, she rapidly closed the distance.

Then, she grabbed the head of the last one with both hands and, twist.

Surprisingly, a person cannot scream when their head is turned so that their nape touches their back.

Not only can they not scream, they can't even breathe, blink, or even think.

It was just that the nape of their neck touched their back slightly.

Yet such truly surprising changes occurred in the human body.

Qing quietly laid down the collapsing figure.

Then, as if nothing had happened, she looked ahead again, and at the back of the one in front.

Qing thought to herself, as if recalling a horror story she had heard somewhere.

Now, you're the last one, right?