\chapter{The Showdown Between Humanity and Ximen Qing (1)}

Ah, shit. I stayed up all night…….

At some point, the scenery of the dense forest seemed faintly visible to the eye.

It wasn't just a feeling.

Dawn was breaking.

Of course, the dense canopy of the primeval forest did not reflect the dimly lit sky before sunrise.

However, since Qing was not a science-type person, she didn't know about the scientific principles of light scattering or that, strictly speaking, the sun had a certain wavelength.

It was just that Qing's superhuman eyes finally caught a very faint, almost imperceptible, level of light and sent a signal to her brain.

Even though it was almost black and white, with only the outlines visible, it was an entirely different level of comfort from the previous night when she had to rely on the flow of the air to detect obstacles.

It's damp, chilly, and I'm tired…….

I wish I could just soak in a hot bath and then immediately throw myself onto a bed.

Yuanjiajie was half jungle.

The characteristics of a jungle were dampness and the nutrient-poor, reddish laterite soil, and Yuanjiajie was no different.

When brushing past the short, miscellaneous bushes, the damp leaves willingly shared their moisture with dry clothing.

So, after circling Yuanjiajie all night, Qing's clothes were damp, sticky, and heavy.

And her feet were even heavier.

Because of Yuanjiajie's year-round fog, the laterite soil under the fallen leaves had completely stuck to her shoes, creating a thick layer of mud up to her ankles.

The mentality of a Master could remain awake for three more days, but still, staying up all night made one feel weary from the very morning.

As such, it was a morning when she felt truly awful.

If I knew it would be like this, I should have just slept on a tree or found a suitable crevice in a rock.

Regret and fatigue, as well as the damp and sticky feeling, made Qing's morning miserable.

However, regret, no matter how early, is always late.

Qing's nature was such that she was not one to dwell on regrets. Instead, she had the easygoing trait of shrugging it off, thinking ‘what can you do, it's already happened'.

Well, the sun's up, so I just need to get out of here, right?

I should hurry up, soak in a hot bath, and sleep.

That was the best personality trait to preserve the happiness of life.

However, it also had a fatal flaw; she never learned from her mistakes because she didn't dwell on them much.

As such, due to Qing's shallow thoughts, active decisiveness, and her easygoing personality, she was a truly baffling character.

She would act carelessly every time, repeating the same mistakes over and over, ultimately wasting more cost and time, yet not particularly minding it, thus quickly forgetting and repeating the same mistakes over and over again.

She was the kind of person who would live like this until she died.

Despite this seemingly hopeless behavior, Qing was a person who had been praised for her work ethic before she had even started her journey in Wulin.

Thanks to her good sense of work and efficiency, as well as her decent ability to plan things out in her head, nine out of ten of her reckless actions ended successfully.

After all, even just being recognized as a young carpenter in Luoyang was not possible with just brute strength alone. It required skill with one's hands and an understanding of how to assemble things.

However, this time was a miss. It was a big failure, one out of ten.

Qing climbed a tree, thinking, ‘Ugh, this tree is so stiff', and then ascended.

The direction of sunrise is east, so south is that way.

Then, carefully descending and heading south through Yuanjiajie for a while…

Now, as the sun hung on the mountain, the morning had dawned with its faded colors, and she finally reached the south of Yuanjiajie, Jinbian Stream-

"There! It's Ximen Qing!"

"It's really her! She really appeared!"

Whooooosh!!!

Yuanjiajie was a basin surrounded by mountains.

The only relatively low area to the south was blocked by Jinbian Stream, a large river about twenty yards wide, and even if one crossed Jinbian Stream, the paths were blocked by Huangshi Peak and Tianmen Mountain.

From the start, entering Yuanjiajie was like being a rat trapped in a jar.

On the opposite side of the riverbank, the sound of whistles urgently pierced the air, causing Qing's mind to snap to attention.

Ah. This is… This seems like a big problem, huh?

For now, retreat.

Qing disappeared into the jungle.

From behind, the sharp sound of a signal flare, like that of a firecracker, pierced the sky.

Qing, delving deeper into Yuanjiajie, racked her brain.

What should I do?

For now, if I hide in the jungle, they can't do much, right?

If I stay quiet and still for about two months, they'll probably think I got away and give up, right?

I'm used to living in the mountains anyway. I'll just forage for food and when the encirclement is lifted, I'll escape.

That was when it happened.

Woof woof The sound of barking dogs could be heard from somewhere.

Since Qing had been in Wulin for five years and had seen all sorts of animals, she had obviously seen wolves, hadn't she?

Wolves don't bark like that, so it was solely dogs barking to be heard by people.

It was an odd phenomenon that appeared despite the fact that there was no biological difference between dogs and wolves.

These fuckers released dogs!

Qing hastily picked up her speed.

Fortunately, although her surroundings were dark, Qing's eyesight was such that it was no different from broad daylight.

Thus, woof woof from behind, then more woof woof from the left, so Qing ran to the right, only for woof woof from the right this time, so she turned to the left…

Suddenly, a large gray dog leaped out from the bushes, blocking Qing's path.

Then, it settled on a stump and bared its teeth at Qing.

Grrrrr…….

"Easy. Good boy. Can you be quiet?"

For now, Qing tried to calm the dog quietly.

Big failure! The dog barked loudly!

Woof! Woof!

After all, it wasn't a learned command, so how could a dog understand human words?

If it did understand, then it wasn't a dog but something else, something that definitely had to be killed.

At the sound, Qing, who had been about to turn her back, paused.

Huh? Why am I trying to run away?

Right. If dogs bark, trackers will come.

But then again, do I, the Transcendent Master who has surpassed the Transcendent Realm, really need to run away?

Didn't I find that those bandit bastards yesterday were just some third-rate thugs?

Before one properly learned martial arts, what was the point of being a Master if one was going to be a bandit?

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Zilongsam was a bandit belonging to the Geon'gon Troupe.

About ten years ago, after his eldest brother, Zilongil, was beaten to death for stealing crops during a famine, he and his second eldest brother, Zilongi, turned to the greenwoods2 to survive.

(Il, Yi, and Sam were the most basic and fundamental way for commoners in Zhongyuan to name their children.)

And then, he discovered an unexpected talent.

He found that he was not one to be robbed, but one to rob.

Thus, he rose to the seventh rank in the Geon'gon Troupe, a fact that could be inferred from the fact that his own brother, Zilongi, was still stuck at the seventeenth rank, far below him.

Therefore, Zilongsam, who was out on the search, was filled with ambition, thinking of this as a great opportunity rather than feeling anxious.

They said it was just a twenty-year-old girl, and it wasn't even an arrest, but a live capture.

If he could be of help, he would be able to learn martial arts from the elders of the main troupe.

That was why he had taken the lead, rather than being held back by the barking of his beloved hunting dog, Jo Jaryong (female, eight years old) and several other dogs.

As he pushed through the bushes, he finally saw his loyal dog, Jo Jaryong, and two other hunting dogs from another troupe. They were standing under a tree that was about three armfuls around, barking fiercely at the sky, woof woof woof.

"Good job, she's hiding up there!"

Judging by the looks of it, the other hunting dogs had arrived, but the search party from that troupe had not yet arrived.

This meant he was the first to find her, so wouldn't this achievement be generously recognized?

What martial art should I learn?

Heavenly Blood Dao Technique? Reclusive Dragon's Ascension Staff? The Supreme King's Divine Palm?

That was Zilongsam's last thought.

This was because Qing's Moonlight Sword, which had fallen from the tree, entered through Zilongsam's head and exited through his groin in a flash.

"Longsam-ah!"

The second brother, Zilongi, cried out at the death of his younger brother, who was ranked above him as the seventh brother.

And that became his last words.

The world spun, the ground blocked half of his vision, and what the hell? After blinking three times, his detached head, which had not yet accepted its own death, loosened its pupils.

Blood spurted from the headless torso.

A rain of blood poured down.

Underneath it, life sparkled in Qing's eyes.

The feeling of being damp and sticky, the feeling of being heavy and sinking to the bottom of the earth, all seemed to blossom vividly at this moment.

"Here, Ximen Qing is here!"

"Ximen Qing? Am I your friend?!"

Thump! Damp fallen leaves exploded as Qing's figure disappeared.

When she reappeared, wham, she was slamming a blackened palm into the head of a bandit.

Crack, the bandit's head shattered like a dropped watermelon.

Then, the remaining bandit, looking directly at her, trembled, holding his sword with both hands.

"Is that… meant to be used as fire?"

"N-No, it is not."

"Ehhh, it looked like you were about to light a fire. But I really hate loud noises, you know?"

"I-I will not light it!"

"You won't? Hmm."

Just as Qing was pondering how to pick a fight, it happened.

Rustle rustle, several shadows suddenly rushed at Qing with rapid footsteps.

Startled by the unexpected ambush, Qing staggered.

It was an attack from the dogs.

One on her right arm, one on her left shoulder, one on her right ankle, and one on her left thigh.

The question was, how many hunting dogs were biting Qing at this moment?

"Ah shit, that's heavy."

Wolves, as creatures, were not very talented at hunting, having only the ability to bite and shake their heads to tear flesh.

That was why wolves, who were always hungry, sought out humans who always seemed full. As such, wasn't it the moment the best friend of humanity, the dog, was born?

At any rate, due to their low hunting success rate, dogs had a knack for aiming for the back of the neck.

Four hunting dogs rushed at Qing's blind spots all at once, displaying an excellent teamwork that overwhelmed her.

But the masters had turned their backs and fled as soon as their beloved dogs had pounced.

Their seventh brother had been split in half right before their eyes, one had his neck snapped, and another had his head smashed.

Their will to fight had long since disappeared.

As such, Qing frowned as she tried to chase after the bandits.

It seemed the dogs bit her thinking she was escaping, holding onto her limbs.

However, it felt like biting into a rock instead of flesh, making their jaws ache and their heads shake without budging as if she was a giant tree.

"You motherpuppers. You think I'm tasty? Huh?"

Qing's mood soured, having missed the chance to initiate a hunt.

The dogs, sensing the ominous tone, slowly released their bite and sank to the ground.

Then, they looked at the distant mountain with the whites of their eyes showing, a unique expression dogs made when trying to read the room.

"Killing dogs is a bit iffy… But you guys are not first-timers when it comes to biting people, are you?"

Killing dogs was frowned upon.

Dogs might feel wronged.

But Qing also killed people who bit people.

In fact, from the perspective of one species versus another, it could be considered a form of respect.

Just as Qing raised her sword…

The quick-witted dogs simultaneously rolled onto their backs, exposing their bellies.

Their thick tails tucked between their legs covered their genitals.

And they continuously let out pitiful whimpers, kiiiiiiiiiing.

It was the ultimate display of complete submission!

"Ah shit, this makes me feel bad."

Qing liked large animals, small animals, handsome animals, and ugly animals.

"Fine. Hey, bark!"

The dogs, startled, looked at Qing and tilted their heads.

This, too, was a unique form of communication that only dogs seemed to display among the same species.

"Bark, I said. Bark, woof woof."

Qing made barking sounds.

At that, the hunting dogs tilted their heads again.

They couldn't understand what this scary new owner was saying, but they knew at least that the display of submission had worked.

The dogs wagged their tails and rushed to Qing, rubbing against her and licking her. Woah, hey, calm down. Even dogs are fucking disobedient.

"Ah, shit, bark, I said! Bark! Woof woof! Woof woof woof! Arf arf! Arf arf arf arf! Awooooo!!"

Qing tried making all sorts of dog noises.

They need to bark for the bandits to come, don't they?

Finally, upon hearing Qing's howling like a wolf, the dogs finally responded with howls of their own, followed by barking that was somehow filled with more joy than ferocity.

-Over there, that way!

Amidst the barking, the voices of the bandits could be heard in the distance, along with the rustling of leaves, cha-ba-sa-rak.

Qing grinned and climbed up a tree. 