\chapter{The Showdown Between Humanity and Ximen Qing (10)}

Qing placed her hands on her hips.

Alright, let's focus.

"I can't do it. I can't do it like this. What in the world is this? You asked me to bear you a son, didn't you? Does someone who asks for a son do this? I didn't expect silk bedding and incense, but at least we should do it normally. I can't do it. I won't do it like this."

"The promise is differen-"

"No, wait, you fed me some kind of aphrodisiac. You're such a coward, afraid that I might do something else. So you want me to take drugs like some kind of animal? You think I'm lower than a beast? Is that it? Honey, is that all I am to you?"

"Hmm?"

"I'm really upset. The neighboring military family decorated their bridal chamber with roses, cherry blossoms, and plum blossoms, so it's hard to tell if it's a room or a paradise. They said the fragrance is so strong that it's almost suffocating. Honey, did I ever ask you for that? Did I ask for a gold ring or any other gift? Is this why you're seeing me? You only care about my body, don't you?"

Qing vented the resentment she had suffered before her departure to this Dou Yougan.

Whether it was there or here, men were all the same, and it was a type of speech that evoked fear from the instinctual domain of men.

"No, it's, it's not like that."

"Then what? You have no other thoughts but that, don't you? You don't think about me, do you? Don't you know how I feel? Do you really not know why I'm like this?"

"I… uh… I'm sorry. I'm sorry."

"You want me to bear a son, right? Does a child just pop into existence with a single thrust? Are you going to tie me up like a beast every time we do it? Why don't you just share me with your precious brothers and their wives when you're bored? What? What did you say? All in the name of loyalty?"

Qing's tongue, an intangible poison that gradually seeped in.

"Is this your idea of loyalty? The woman who will be the mother of my child, what was that? Why, after your son is born and grown, you'll bring him here and point at this animalistic mating contraption, saying, ‘This is where your father tied up your mother like a beast and forced himself on her. Her screams were so loud, it was deafening. You should tie up a woman you like here too'."

"Stop. I'm sorry. I was wrong. I was thoughtless, so stop, please stop."

At that, Qing sniffs, as if she had been crying.

At the same time, she exerted force on her vocal cords to add moisture to her voice, making it sound like she was crying.

"I, this is my first time. It's my first time, you know. But this is too much. How could you do this? How could you do this to me?"

First time!

Could there be any other word that could make a man's heart pound like this one?

Dou Yougan was flustered.

"I, uh, you were acting so bold, so I thought you had some experience. I didn't know you were so concerned about this."

"That's too much. Really, how could you say that?"

"I'm sorry. I misspoke. Well then, rest well today, and tomorrow I'll prepare properly……"

"Alright, then hold, hold my hand."

Qing said so and held out her hands.

For some reason, Dou Yougan felt a strong urge to hold them.

After all, wasn't the atmosphere right for it?

Dou Yougan hesitantly reached out, and Qing grabbed his hands, interlocking their fingers.

Then she smiled, a radiant, dazzling smile as if spring had fully bloomed.

Dou Yougan's pupils dilated.

Without realizing it, he opened his mouth wide, feeling the slender bones between his fingers and their unusually cold touch, softer than any silk in the world.

Dou Yougan had never been particularly interested in women and had no interest in sex.

He had secretly worried if there was something wrong with him, but now he knew.

It wasn't that he wasn't interested in women, but that he hadn't met a woman he was interested in.

His heart pounded as if it would burst, and now, at over fifty, his worn-out heart was moistened with a certain emotion. First love. This must be first love.

Perhaps sensing the pounding of his heart, Qing's expression turned shy, and then alluring.

And in those large eyes, so large that they seemed to reflect his entire being, a longing gaze appealed to Dou Yougan.

And her lips seemed to be saying something, no, not saying something.

Her slightly parted lips, as if thirsty or out of breath. Those lips, yes, those lips.

Dou Yougan instinctively knew.

Now was the time.

Dou Yougan slowly leaned his head forward.

Lips and lips drew closer.

Qing also instinctively knew.

Now was the time.

Simultaneously, Qing's knee shot up.

It was a fierce collision between the kneecap and the pelvis!

Since the two were of similar height, but Qing's waist was a span higher, it was a perfect blow to break the lineage.

In between, something that was supposed to prevent the two from touching went squish, and.

"Keoheuk."

Even if it wasn't the Unrestrained Realm, but the grandfather of the Unrestrained Realm, no one could withstand the pain of having their gender forcibly changed.

Dou Yougan's eyes rolled back in his head, revealing only the whites.

"I hate rape! I like pure love! Think from a woman's perspective! So I'll make you a woman! Then you should have two holes, right?"

Qing's foot returned to the ground and then stomped up again.

Crack!! This time, it was a proper sound of bone against bone, and Qing's knee felt sore.

Wow, he's an Unrestrained Realm Master, so even in this situation, his resilience is no joke.

Despite the agonizing pain, Dou Yougan's hands struggled to escape.

However, the white hands with interlocked fingers were as strong as the White Hand Demonic Arts could make them, and its owner was Yeohangjeok, who had the strongest grip strength among all humans.

In fact, strictly speaking, the term Yeohangjeok was incorrect.

Even the strongest historical figure, Xiang Yu, was weaker than Qing, so she shouldn't be called Yeohangjeok.

It would be more appropriate to call Xiang Yu Namcheong.

Xiang Yu was just an ordinary, muscular man who happened to exist before Qing was born.

Qing pulled both her hands down, twisting his arms as if wringing a rag.

She felt a strong resistance, so she tilted her head back, then forward, bang!

The sensation of a broken nose spreading through her forehead. Ah, this is addictive.

A man's nose size is said to be proportional to his ‘lower region', though there's no evidence to support this theory.

Whether it's part of physiognomy, she wasn't sure.

But now, that theory had been proven.

After all, both the upper and lower regions had been crushed.

"Argh!"

At the moment the pain weakened his grip, crack, crack, crack!

The delightful sensation of numerous bones breaking and tendons rupturing was felt, as Qing's interlocked fingers reached Dou Yougan's wrists.

This meant three fingers dislocated, wrist fractured, and a chain reaction of tendon ruptures.

Left hand and right hand, one plus one.

Qing's sense of slaughter was always generous.

"Does it hurt! I'm not in pain! Are you jealous?!"

Thud!!

This sound was from the collision of Qing's right foot and Dou Yougan's shin.

Thud! Thud! Thud! Thud!

With both hands completely mangled and held, there was no room to dodge, standing face to face. Moreover, he couldn't possibly regain his senses due to the shock and pain of the sex change operation (from male to neuter), followed by the nose job and the compound fracture of his hands.

"Hey! What's with! Your! Bones! They're! So! Tough! Did you! Drink! A lot! Of milk! Or something?!"

Crack. Finally, the sound of a rupture was transmitted through her toes!

The enemy's shin, defeated!

"Here's a question! What's a hand-cripple plus a foot-cripple?"

Qing giggled, excited.

"Huh? You're saying it's you? Nope. Wrong. Of course, you are a hand-cripple and a foot-cripple, but did I make just one or two of those? Wrong, so here's a penalty. Let's do the spin!"

Qing spun in place.

It was a violent way of playing that fathers often did with their children, usually resulting in getting their backs slapped. That was exactly what the spin was.

However, Dou Yougan was quite heavy for spinning, but this was solved by the fact that Qing's strength transcended human limits.

Qing spun with her hands firmly interlocked.

Normally, she was already a bit crazy, but now she was spinning very fast, a truly crazy bitch, if you will.

Dou Yougan's body was horizontal to the ground, orbiting around Qing.

Trivia: Fingers do not have muscles.

Compared to Dou Yougan's weight, the centrifugal force that skyrocketed was only supported by weak flesh at the already dislocated and ruptured joints.

As a result, even though Qing didn't let go of his hands, Dou Yougan's body, on its own, escaped its orbit and was launched at an incredible speed.

Crash!!!

It was an incredible impact, befitting the incredible speed.

Huh? I didn't let go, though.

As Qing looked down at her hands, she saw that Dou Yougan had abandoned six fingers and left.

"Oh my, why so hasty? You could have enjoyed it more."

Qing walked slowly towards Dou Yougan.

Looking at Dou Yougan sprawled on the floor, Qing realized something quite astonishing.

My goodness, this is just like the Young Master!

Wow, shivers, shiiiiivers.

Fingers scattered, one leg with a broken shin bone sticking out.

The first son of the Chaeju and his first subordinate had been attacked by the same person and ended up in the same state.

What a twist of fate, what a remarkable coincidence!

Isn't this something that would be featured on a Sunday morning show, like ‘Surprising!'?

You know, with the ‘Why, however!' and all that.

Of course, the Creator in Zhongyuan did not work for six days and rest on the seventh, so there was no concept of a week with seven days.

Therefore, there was no Sunday and no weekend.

Of course, being a primitive and uncivilized civilization, they didn't have screens to stare blankly at when bored, so there was no ‘Surprising!' either.

"Keoheuk."

Lying there like a broken doll, in a pose that could be considered avant-garde, Dou Yougan coughed up blood.

But it seemed his senses had returned.

"Why, why……?"

"What do you mean why? You need to ask proper questions."

"Why did you, the promise, it wouldn't be bad for you either……"

"Oh, you're still not getting it. Hey. Imagine you're in my shoes. Suddenly, a pederast comes up to you, saying let's sleep together, give me just once. Then he says if you do, he'll let you escape. Would you want to kill him or not?"

"Ah."

Dou Yougan understood in an instant.

It was the greatness of thinking from another's perspective.

A bitter smile formed on Dou Yougan's lips.

"Then, how could we have had a relationship that wasn't, cough, coulock, bad?"

"Well. If you had met me then and said, ‘I'm tired of being a bandit. I want to live a new life. So let me help you clean up this trash. Let's defeat the Chaeju together and burn down those bandits', then I might have accepted you as a comrade?"

"I see, that could have been possible. Why didn't I think of that? It still wouldn't have been bad. After all, I planned to let the child live a life where he wouldn't be looked down upon like me, even though I was doing this."

"Well, it's because you lived your life extorting others through threats. Saying ‘give me your child or you'll die' is no different than saying you'll spare their life if they give you their child. You were just being a bit more euphemistic. Alright. Enough chitchat."

"If I'm going, please make it comfortable."

Dou Yougan closed his eyes tightly.

However, despite his compliant attitude, his inner thoughts were filled with malice.

Come closer, come closer and reveal a gap to end my breath in one last moment.

Even if he was an Unrestrained Realm Master, his body would become a weapon if he just wrapped it in Sword Force.

Although his fingers were gone and his hands were dangling, if he could just swing them like a hammerhead, if he could just disrupt her posture once.

I guess I should just cut off her limbs so she can't run away and keep her confined.

Yes, come to think of it, there's no need for the mother's limbs to make a child.

And I don't have to be the only one to use her, right? The Chaeju also needs a new child.

No, that won't do. Mine. She has to be completely mine.

If I cut off her limbs, clothe her, feed her, and put her to sleep, eventually, she'll depend on me and open her heart, right?

She will be completely dependent on me, unable to do anything without me, and will cry and make a fuss when I'm not around.

That's perfect.

Dou Yougan hid his dark thoughts by closing his eyes. He focused on sensing the distance and presence.

It was utterly despicable, but with both hands and one leg broken, there was no way to win against an Unrestrained Realm Master except through a surprise attack when their guard was completely down.

So, what else could he do?

However, Qing's voice, sounding as if she found something ridiculous, made him open his eyes again with a start.

"What are you talking about? With all that's happened, how can you expect a comfortable death? I heard this place has good soundproofing? That's great. I doubt an Unrestrained Realm Master would just die without a fuss. Let's see, is there an iron here? And a furnace? Ah shit, my sword is upstairs, too. Where could I tie you up, ah. Yes, let's try that thing. What should we call it? The beastly mating device? Anyway."