\chapter{The Showdown Between Humanity and Ximen Qing (11)}

Creak, the sound of the iron door opening. A-Qing, bathed in the sunlight of the outside world, had a remarkably bright expression on her face.

Wow. I never knew the sun could be so welcoming.

Maybe it was because she hadn't seen it in a while.

Although Zhangjiajie was known for having around 250 cloudy, snowy, rainy, or foggy days a year, the remaining 100 days were clear.

It seemed like today was one of those days, or perhaps it was due to her lightheartedness; a feeling of relief as if she had been reborn.

However, contrary to her Daoist-like, serene expression and the tranquil gaze that seemed to exude the scent of pine, she was covered in blood from head to toe.

She even had a severed human head tied to her waist by its hair.

People often called such individuals 'madmen with clear eyes'.

It also meant that they were far more dangerous and unpredictable than those who were simply out of their minds.

A-Qing tapped the head at her waist and spoke.

"You like the sunlight too, don't you? No matter how good the scenery is, if it's always foggy and gloomy, people's personalities will rot, you know? Like mold growing. Well then, let's claim the victor's spoils, shall we?"

She had heard that the Liangshan Marshals were the elite-of-the-elite fighting force of the bandits.

Somehow, hearing they were an elite fighting force made her feel like things wouldn't go her way. It was as if these guys wouldn't even be able to hold chopsticks properly.

Regardless, since she had defeated their leader, she had earned the right to claim the stronghold's wealth.

Since they were supposedly the most decent among the bandits, she hoped they would have something good.

Maybe even a Secret Manual or something?

I'm not even hoping for something Purple. Just a Gold would be fine.

And…

"Hmm. Fucking nothing."

A splendid haul of absolutely nothing.

Qing had underestimated the bandits.

Storing valuables in their personal quarters required a minimal level of ‘trust'.

At the very least, it required the basic trust between humans that their comrades, or brothers in bandit terms, would not rummage through their belongings and steal from them if they entered their rooms.

But what trust could one have among thieving bastards?

Since they couldn't even trust each other, they either carried their valuables on their person or hid them in some secluded place. After all, if they left them in their rooms, someone could just snatch them away, only to be mocked later as a thieving bastard who got robbed.

For that reason, Qing only managed to add some miscellaneous items to her belongings, which she had casually placed down during disarmament.

Isn't this not supposed to happen?

She had defeated a Master of the Unrestrained Realm, and without using martial arts, only pure physical prowess at that.

Moreover, it was a fair and square, head-on confrontation.

Even if she was only at the Early-Stage Transcendent Realm, it was still a great challenge that would have been difficult to achieve. And she had accomplished something that was at least in the top 1% of achievements, only to gain nothing from it.

Could this even be considered possible?

So, to soothe her upset feelings, Qing decided to use fire as therapy.

Call it fire-gazing?

When one stared into a fire, the filth and wounds of the heart seemed to burn away along with it, leaving a sense of tranquility.

Indeed, fire. Fire, I say.

Everything foul must be burned away.

Seol-A, are you watching?

I'm doing well like this.

Though I can't remember Seol-A's confident appearance from back then, her spirit still lived on in my heart.

Thus, having healed her heart with fire, Qing made a splendid exit, leaving the blazing Liangshan Marsh behind like a protagonist in a story.

Qing tapped the head at her waist.

"Let's go, Du Yousan. Let's go back to your leader. I couldn't carry your body because it seemed like it would spill, so I only brought your head, but it's still okay, right? Why was it in the Three Kingdoms? Guan Yu? Lord Guan, why did you only bring your head? Well, Du Yousan, you've practically evolved to Guan Yu level from being a bandit. That's like a super-fast promotion. You're grateful, aren't you? You don't need to thank me. I enjoyed it too."

Du Yousan's head, stiffening in rigor mortis, was filled with the vivid horror of a death where he couldn't even close his eyes due to the sheer agony.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

"Aaaargh! Ahhhhhhh! Ran-ah! Su-ya! On-ah! No! No! This father! This father is……!"

Inside the tent, a scream that sounded like the tearing of blood erupted.

Even outside the tent, where there was nothing within a radius of five zhang, the bandits standing guard at the very edge rolled their eyes.

For reference, the act of rolling one's eyes was the most universal human expression of anxiety.

"Is this okay?"

"I heard the guys who stood guard last time at the Golden Banners Stronghold were all torn to shreds."

"I don't think I can keep doing this bandit thing anymore. It's too nerve-wracking."

"What are you going to do if not banditry, Brother Nam? Do you have any skills you've learned?"

"Well, maybe a ronin……"

"It's better to be a bandit than a ronin. Much better."

The two bandits standing guard were from different strongholds, so they called each other Brother Nam.

They were Brother Nam because they were Southern.

Of course, they were also Brother Nam because their realms were similar.

If a low-level bastard dared to call someone Brother Nam, he would be beaten like a dog and taught some manners.

Meanwhile, Mountain Brain, Ah Zandeok, was contemplating.

Should I really keep playing strategist for the bandits?

Every time he made a report, it felt like walking on a tightrope, as if his head might get smashed in at any moment.

It was obvious that the culprit who killed the leader's third daughter and burned down the main stronghold was none other than Ximen Qing, not some follower of the Blood Cult.

Now, his hypothesis was almost over 90% confirmed.

At this point, it was closer to certainty than a hypothesis.

This was because in the past few days that the stronghold had burned down, not a single person had witnessed Ximen Qing during the search of Wŏnjiājiè.

Moreover, the traps that had been set were not being repaired.

But how?

Did she have a way to secretly escape from Wŏnjiājiè from the beginning?

Then why did she not run away and remain there?

"Of course, she must have a grudge against the bandits……"

Her excessively cruel methods, the act of burning down the stronghold, and how she slaughtered the bandits like a demon of carnage.

However, Ah Zandeok was the Mountain Brain.

If he messed this up, the increasingly deranged Chief would definitely not let him die peacefully.

So he had to either capture Ximen Qing…

Or run away now and cut his losses.

Honestly, he wasn't confident.

That elusive, clever, yeah, the problem was that this bitch Ximen Qing was really smart, with excellent schemes and resourcefulness.

If Qing had heard Ah Zandeok's inner thoughts, she would have said something incredibly shameless like, Hehe, what are you talking about? I've often been told that.

"But where did this Du Yousan go? I was going to try to persuade him that even if the Liangshan Marshals were crushed, it wouldn't be a big deal."

Now, Ah Zandeok could only think of extreme luring tactics.

Unless she suddenly turned stupid and blatantly appeared before his eyes, saying, ‘Here I am, come and get me!', there was no way to catch her.

That was when it happened.

"Mountain Brain! Right now, right now!"

"What is it, in the middle of the night?"

"Ximen Qing! Ximen Qing has appeared!"

"What? She burned down a stronghold, and it was Ximen Qing? Is there any proof?"

"That's not it, Ximen Qing! Ximen Qing has appeared!"

At that, Ah Zandeok blinked his eyes.

What? Really? She suddenly appeared?

Saying, ‘Here I am, come and get me!'?

"Where, where did she appear!?"

"Across the river!"

"Immediately, immediately guide me!"

Thus, by the time Ah Zandeok rushed over, countless bandits of the Green Forest had already gathered by the river.

On the other side of the pitch-black night, across the pitch-black water that was like the Yellow River, was Qing.

Of course, for Ah Zandeok to see Qing meant that there was a light source illuminating her, reflecting her dazzling beauty into his eyes.

So there was light shining on Qing.

A large bonfire, or rather, a huge brazier, had been lit, brightly illuminating the surroundings.

And about two zhang beside it, several smaller bonfires were lit, where Ximen Qing was cooking. What? Cooking?

Ah Zandeok doubted his eyes.

But whether he first saw it, blinked and saw it again, or rubbed his eyes and checked again, she was still cooking.

With a wok and a frying pan that had been brought from somewhere, she had skewered meat on one side, neatly angled so it would cook evenly, and was busy stirring soup in a pot, shaking the pan, and moving around busily.

Then, Ah Zandeok had a great realization.

Even if she suddenly turned stupid and blatantly appeared before my eyes, saying, ‘Here I am, come and get me!', there was no way to catch her!

Because of that damn river!

Suddenly, he felt a surge of heat.

He was suffering so much because of her.

But there she was, acting as if she had come on a picnic, cooking and all.

"You bitch! Ximen Qing!"

"It's dangerous!"

The moment Ah Zandeok shouted, someone immediately pulled him back, and a moment later, something whizzed past with a sharp whoosh!

"W-What was that just now? An unseen weapon?"

"It's a rock. If you get hit, it really hurts, and if you're unlucky, you end up like that guy over there."

The Liangshan Marshal who had pulled Ah Zandeok pointed to a fallen comrade with his hand.

The blood oozing from his head glistened, reflecting the torchlight.

"A rock? Throwing a rock? Is it some kind of secret assassination technique? Infusing it with Inner Qi-"

"I tried blocking one, and it's just a purely hard-thrown rock. Besides, if you infuse a brittle rock with True Qi, even a Transcendent Realm Master would tire after throwing just a few, you know."

The width of the river was roughly fifteen zhang.

Since they weren't right at the riverbank, the distance was over twenty zhang, but the thrown rocks were flying straight like taut strings.

So it was only natural that if it hit the head, the head would burst, if it hit the bones, the bones would break, and if it hit the flesh, it would bruise.

Qing had thrown one and admired her own throw.

Wow, if I were a pitcher, I could throw twice as fast as the human record.

At this rate, I could even win against an eagle. Wow, holy shit, I'm crazy in retrospect.

Come to think of it, people with status windows or similar abilities should never be allowed to participate in sports.

They're far worse than druggies, complete scumbags under the heavens.

Anyway, after giving a stern warning with the power of the earth to the bastard who dared to utter profanities during her sacred cooking time, Qing focused on cooking again.

Since no one else was shouting, she thought, ‘Where's the Chief? Isn't it about time for him to show up?'

After all, if they were informed of such a situation, their heads would likely be at risk, so they were intentionally delaying and not reporting.

Thus, Qing finally finished cooking.

And then, the most promising candidate for the title of the Greatest Flavor Under Heaven began a performance of the advanced civilization, an eating show.

Qing ate well.

There was no need for further explanation.

A cooking and eating show unfolding in the middle of the night.

In a way, it was a cruel act.

On the other side of the river, the bandits could only swallow their saliva.

"Ah, right! Hey, are there any of Liangshan Marshals' elites over there? Thank you so much for sharing the cooking tools and ingredients! Thanks to you, I'm eating well!"

Qing had taken the things from the Liangshan Marshals.

There were plenty of grains, as well as various seasonings such as salt and spices.

However, she left the meat behind because she felt it was unsanitary, and she caught a few birds along the way.

Birds were easy to catch with a thrown stone and were also a great source of protein that guaranteed a certain level of taste.

"What, what did you say!?"

Ah Zandeok was startled and looked at the Liangshan Marshal.

Sharing? Could it be that the Liangshan Marshals were in cahoots with Ximen Qing!?

"I-I don't know anything about this."

"But didn't she just say so? Hey, Leader, where is Du Yousan? Why isn't he showing his face at a time like this!?"

"I don't know either."

"Ah! Over there! You're looking for Du Yousan!"

Ah Zandeok was startled again.

He hadn't lowered his voice.

But how could she hear him from over there and even reply?

However, he couldn't think further about Qing's mysterious hearing due to the following words.

"You don't have to look for him over there! He's here with me!"

"What!? Du Yousan, the leader of the Liangshan Marshals, has betrayed us!?"

"He tried to betray us. But he couldn't. Because I didn't let him. Now, everyone! This is Du Yousan! His body isn't in great condition, so unfortunately, only his head is here to greet you!"

Qing grabbed the hair at her waist and lifted it up proudly.

"Lies! It's all lies! Where did you get that head to try and deceive us! Senior Brother is a peerless expert of the Unrestrained Realm!"

"But he was weaker than me, you know? Now, if you don't believe me, check for yourselves!"

Qing held Du Yousan's head with both hands and pulled it between her legs, then, Heave-ho!

Du Yousan's head drew a large parabola high, high up into the sky.

At that, someone leaped up gracefully, catching it in mid-air.

Why catch it so gracefully when I purposely threw it upward in an ungraceful way? How rude.

"Se-Senior Brother! Senior Brother!"

Perhaps he was close to Du Yousan, as he immediately shouted in shock and despair. 