\chapter{The Showdown Between Humanity and Ximen Qing (3)}

Ah Zandeuk had received a request to capture Ximen Qing alive. It was a ‘request' from the Grand Commander himself.

It was a heartfelt request from the very same Grand Commander who always told him to use that scamming head of his, calling him a fucking swindler every day.

So, Ah Zandeuk thought that if he created some sort of debt with the Commander now, wouldn't his future in the Nokrim be more comfortable? As such, he racked his brains for all sorts of schemes and plans.

However, humans are creatures who think based on the common sense they know and the foundations they believe to be obvious.

No matter how much of a Transcendent Realm Master one was, they wouldn't be able to endure forever in this harsh forest.

Most of the year, the primeval forest was so humid that fog would form.

Now that it was early November, the nights would be cold, and the humidity in the air would make it difficult to maintain body temperature, making the perceived temperature even colder and harsher.

Therefore, they would send out grunts during the day to keep her moving and block the paths at night to prevent her from escaping.

And if they just left her like that, the weather would only get colder.

Wouldn't she just collapse from exhaustion, hunger, and the cold, or try to break through the encirclement before that?

That was when the elites of the Nokrim, which had been saved up, would make their move to subdue Ximen Qing and deliver her to the Grand Commander.

No, in the first place, the Grand Commander would rush over himself, so there would be no need to deliver her.

For advice on this plan, he sought out the second-in-command of the Nokrim in terms of realm, as well as the third-in-command in terms of ranking, the Great Chieftain of Liangshan, Dou Wusan.

He asked how long a Transcendent Realm Master could endure in such a harsh forest.

He also asked if someone in the Transcendent Realm could be fine even when the cold wind was blowing, and whether they could activate their Inner Qi to burn off the poison if they ate poisonous mushrooms or were bitten by venomous insects or snakes.

Dou Wusan, who was at the Early Stage of the Unrestrained Realm, confidently replied.

"How could that be possible? They might be able to endure for a few days, but after ten days, their stamina and Inner Qi would be at a dangerous level."

Dou Wusan also answered based on his own subjective experience, tailored to the level of an Early Stage Transcendent Realm.

And so, the overall evaluation of the first day of the operation.

It was not bad for a start.

Ximen Qing must already be quite exhausted from setting up traps overnight.

Points for improvement.

Identify which bastard ordered the daytime insertion teams to be supplied with food and give the bastard who helped the enemy's supply an appropriate punishment.

Unfortunately, the bastard who helped the enemy's supply was right beside him.

But there was no way he could punish the Great Chieftain of Liangshan, so he had no choice but to use nice words to say that they should not give food because Ximen Qing would be prevented from looting their supplies.

"How could you not even provide a single meal when sending them into such a harsh forest?"

"Didn't seventeen of them enter and not return? If only ten of them were captured, that would be thirty rice balls. If that woman ate sparingly, that alone would be a month's worth of food. It will become spoiled before that, but thanks to this, the operation period has been extended by at least ten days."

"Ahem."

Dou Wusan realized his mistake at those words.

As such, he had no choice but to change the subject awkwardly.

"Ahem, ahem, even though it is still early November, the night chill is quite unusual this year. She must be shivering and suffering by now, so no matter how much she tries to endure with those rice balls, how long will she last?"

----

"Ah, it's so warm and nice. You guys are surprisingly helpful, you know?"

Inside a shallow cave within some peculiar rock formations, Qing was nestled in fur, giggling as she had a hunting dog on each side of her legs and flanks.

"But, um, ugh, the smell. Is it you guys, or is it you, Mr. Bear?"

K'hu…… The bear, supporting Qing's back, let out a resentful breath. Qing had given him the name Mr. Bear.

She had stayed up all night yesterday, so she thought she should get some sleep tonight. After all, as an expert in outdoor sleeping, Qing could tell the condition of the forest with just a glance.

The dew even reached the parts where the leaves were piled up.

That meant that if you pressed down on the lower part, it would be so soaked that water would just ooze out.

You can't sleep on such ground.

Because it's damp…….

Thus, before sunset, Qing diligently searched for a place to sleep.

After all, there were many peculiar rock formations around, weren't there?

There should be a concave spot on such bedrock, a stone floor that wouldn't be wet.

Then, she unexpectedly found a good cave. Just as she was about to step inside, the four dogs, which Qing had renamed Whitey, Yellow, Blackie, and Spot(formerly known as Zhao Zilong), blocked her way, growling and baring their teeth at the interior.

Whitey was white, Yellow was yellow, Blackie was black, but she didn't know what to call the gray dog.

However, since it had white round spots above its eyes that looked like eyebrows, she named it Spot.

She thought there might be something inside and tried to enter, but they whined and held onto her pant legs. She thought, ‘Do you think you can stop a human just because you're mere dogs? You bite, I go,' and dragged them in.

And there was a bear that had just entered hibernation.

Even for an animal, waking up from sleep is an unpleasant experience.

Even though it was somewhat sluggish from just waking up, a bear's strike was still powerful enough to crush a bull's head.

The blow landed on Qing.

In return, she beat the shit out of it.

A Master's fist really hurts.

It was a pain the bear had never felt before.

The shock absorption provided by the bear's thick hide, the layer of fat underneath, and the elastic muscles was enough to withstand falling rocks.

However, if a fist filled with Inner Qi struck with the profoundness of the Open-Back Fist, both bears and humans would burst into tears because it hurt so much.

Bears were also quite intelligent creatures.

It instinctively realized that it would die if it fought back, so it suppressed its temper, sat quietly, and carefully watched Qing's reactions.

Thus, as it obediently lay down as the human pushed it, fortunately, there was no further harm done as she just laid on its torso.

Wolves were not allowed on the back of a bear, the mountain king (though tigers might disagree). To a wolf, such an act was an intolerable insult.

But the human was scary, so it endured.

Thus, Qing was very satisfied.

Since it had been preparing for hibernation, it was fluffy and better than any bed, and although there was no blanket, the hunting dogs covered her with their bodies, providing warmth and a pleasant sensation of a cute, fussy heartbeat.

Just one thing, though. She could do without the smell.

"Hmm. It's tiring since I stayed up all night, so there's no helping it. I think I'll have to find a stream and wash up a bit tomorrow. All of you really smell like dog……"

Tired from staying up all night, Qing quickly drifted off to sleep, almost like fainting.

And so, from Qing's Mountain Diary.

\begin{quotation}
	
Day 1.

{\itshape Today, I ate rice balls and went around setting up traps.

Since there were nets among the spoils, I tried setting up traps using them. Then, those bandits brought dogs again.

How dare they try to abandon dogs. I cannot forgive that. Death penalty.}\\

Day 4.

{\itshape There are already eight dogs.

I'm running out of rice balls, so I might need to catch some wild animals.

Still, with eight of them, it's warm when I sleep since they cover my whole body.}\\

Day 6.

{\itshape Today's dog count is eleven.

With nothing to do, I wandered around setting up traps, hoping to find something tasty. Now, the bandits are only sending dogs without showing up themselves.

I hear cries here and there, and when I go, they are always pierced by something.

Did I set up too many? It's not fun at all.}\\

Day 7.

{\itshape Caught a wild boar.

A baby boar was so cute and small that I petted it a bit, and then a big one appeared and charged at me.

Honestly, I looked down on it, but it hurt quite a bit.

The boar's charge was stronger than Mr. Bear's.

In a fit of anger, I unconsciously flicked its head, and alas, I didn't realize a pig's skull was so weak.

I wish I could have roasted it, but it was too much of a hassle to start a fire, so only the dogs had a feast.

Wild boar meat isn't that tasty, so it wasn't worth the trouble of starting a fire.}\\

Day 8.

{\itshape Today's dog count is thirteen.

And for some reason, a pack of wolves I met on the road started acting cute and following me around.

As such, I now have eight more wolves.

They say dogs and wolves are practically the same species, so in total, that makes twenty-one.

It's a real dog party. A dog party.}

\end{quotation}

And so, on the eleventh day…

Qing's patience finally exploded.

I can't live like this anymore!

It has already been more than ten days since I stopped eating hot food!

I'm not some Daoist cultivating the Dao, so how can a person live on just a vegetarian diet?!

The rice balls have all gone bad. I could eat them if I had to, but I'm so sick of them that I just can't anymore!

Honestly, being unwashed and icky is something that one gets used to after a few days. It even becomes comfortable after a certain limit.

Sleeping has also become quite warm, even sweaty, as the family has grown.

Mr. Bear didn't like that his hibernation spot was getting more and more crowded with family members, but in the end, he seemed to have given up and just went into hibernation, not caring who came or went.

So there was no intended inconvenience.

But I can't stand this shitty diet!

Thus, the enraged Qing roamed the forest, caught a roe deer and two pheasants, threw the deer to the dogs and wolves, and made a huge fuss about starting a fire.

It wasn't that she couldn't start a fire in the wet forest, it was just a hassle.

First, she had to find dry wood to start the fire, which involved splitting wood to find firewood that was still dry on the inside.

She then carefully shaved the dry wood with the edge of her Qingzha Sword, piling up the shavings. After that, she struck a flint to light it and blew on it, going, ‘Oh, it caught. It caught.'

Then, she added the less dry firewood that had its exterior cut out, but it took a long time for the fire to catch.

It took over an hour to start a campfire, which explained why Qing had been reluctant to do so all this time.

Once the fire was big enough, even somewhat wet firewood would burn.

However, this had the downside of producing an enormous amount of smoke.

Well, let's just think of it as smoking the meat.

She didn't know what kind of tree it was, though…….

As Qing was roasting the pheasant, the thick smoke from the burning greenwood rose, piercing through the dense canopy of leaves overhead and billowing upwards.

The Mountain Gate's Strategist, Ah Zandeuk, saw the smoke.

"Alright! The time has finally come!"

"Time? Do you mean it is time to go and capture Ximen Qing?"

"Didn't that bitch start a fire?! She must be cold and hungry, unable to endure any longer!"

She wasn't cold or hungry.

She just didn't like the taste.

"Look at her actions until now. She hasn't shown herself since some time ago. Isn't it obvious that she has become weak and is just relying on traps?"

This was also incorrect.

She was just lazing around because everything had become too much of a hassle.

She had tried various traps and such, but she ended up having too much fun.

As a result, the bandits just followed the dogs and got caught in the traps, ending up with their throats slit. As such, there was nothing fun to do even if she went out.

"And yet, she hasn't started a fire until now, so it must be because she was desperately trying to hide her location. But she must have decided that warmth was more important than hiding, so didn't she start a fire?"

If Qing had heard this, she would have asked what kind of crack house this was and how such an idiot could have scammed his way through life.

But Ah Zandeuk's judgment was based on solid common sense.

Could anyone have imagined that a young woman of twenty had already reached a level where the cold didn't affect her and she just had to huddle to sleep?

Even if someone told him that Qing was now the leader of a wolf pack and was staying warm, he wouldn't believe such nonsense.

On top of that, no one could possibly know that she was a monster who was immune to all poisons, who could eat dirt without getting sick, if not actually digesting it.

"Since she is sufficiently weakened, we should be careful when capturing her alive."

"Hmph, who do you think I am? Even if she wasn't weakened, a mere girl who has barely reached the Early Stage Transcendent Realm is hardly a problem. It's more of a concern that you might get too excited and accidentally kill her."

The Nokrim's Grand Commander, who had been grinding his teeth, made a weeping sound upon hearing the news.

Finally, Won'ga-ya, Wonchu-ya, this father will hold a grand ritual for you, using your enemy as a sacrifice.

Thus, all the forces of the Nokrim under the Grand Commander's command simultaneously entered the Wongye Forest.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

A dirty, homeless woman was roasting a pheasant.

Her damp clothes were so dirty that it was hard to discern their original color and they were covered in animal fur, making her look like a mess.

Since her torso was like that, her face was also probably dirty, but it was hard to tell exactly because she was wearing a veil.

But even if a beauty's appearance is dirty, she would still be a beauty.

So even if she took off her veil, her beauty would not have been diminished.

Thus, Qing was humming a merry tune as she rotated the pheasant skewered on her Moonlight Sword (No. 10), roasting it to perfection.

She had already roasted and devoured one.

After eating it all, she decided it wasn't something to be saved. Since she had already started a fire, she might as well roast the remaining one, too.

And around her, a real dog party had broken out.

Full from the roe deer meat, the canines were playfully biting, pushing, rolling, and tumbling around with bones in their mouths.

It was then.

Suddenly, the dogs all perked up their ears at once, stood on all fours, and bared their teeth