\chapter{The Showdown Between Humanity and Ximen Qing (15)}

Let's just observe the situation for now.

Qing submerged herself deeper into the river by pushing her fingers into the riverbed.

She roughly estimated that she was in the middle of the river's width when her bronchial tubes, deprived of air, felt like they were twisting and warping.

Qing's head popped out above the pitch-black water.

Hoo-eop, hoo, hoo-eop, hoo. Her oxygen-deprived brain gasped for breath.

"Find her! Find her! Bring her to me alive!"

On the other side of the river, Wang Cheolgun was going berserk.

Qing turned her body around by waving her arms.

And on the riverside of the Green Forest…

"Find Ximen Qing! She must be drifting, half-dead with severe injuries! Whoever finds her will be granted all the rewards they desire!"

A man with a goatee yelled at the top of his lungs.

Qing was bewildered.

How could someone who can't even infuse his voice with Inner Qi possibly have the authority to give orders like that?

But absurdly, the Green Forest bandits suddenly became emboldened, as if they had become elite warriors who could take on a hundred men each. They roared and jumped into the river, splish-splash, causing a commotion all over the place.

What the hell? Is this some kind of public swimming pool or something?

At this rate, the river will be half people, half water and overflow.

Qing took a deep breath.

Her lungs inflated. Ow, the pain in her ribs, where she had been hit by the hammerhead, surged.

Ah shit, I don't know what state my wounds are in right now.

Qing's head sank.

She pushed her fingers into the riverbed and propelled herself forward, gliding a full length each time.

Thunk!!

Qing's forehead slammed into something hard.

A few bubbles leaked from her nose.

She had been diving with her head down to check the riverbed, and ended up ramming her forehead into a rock, delivering a nuclear headbutt to herself.

Not just her breath, but also tears welled up.

It was pitch-black at night, and the water was murky. On top of that, it was a muddy river that was unique to Zhongyuan rivers, so she couldn't see anything.

If she could see ahead, her beautiful, sharp, and perfectly shaped nose would have been crushed and bent. In a way, it was better to have a bump on her forehead instead.

Ah shit, it hurts like hell.

Qing frowned and felt around the riverbed.

Then, suddenly, something caught on both her shoulders. Sploosh, something fell into the water, gently pressing down on her back.

Agh!

Although she was pushed on the back, her torso was caught between something and the riverbed. Her ribs were compressed, and her mind went blank for a moment from the excruciating pain as the air was knocked out of her lungs in one go.

Qing instinctively stood up, and since she had almost reached the shore, her upper body emerged from the water with a splash!

The splashing and thrashing sounds turned into dripping water, and an angry voice erupted from behind Qing.

"Hey, can't you watch where you're going?!"

Now she realized that what had caught on her shoulders were someone's feet.

They had caught on both shoulders of Qing, who had been darting through the water like an arrow, and she had dragged the person along with her before pressing him against her back.

Flames erupted in Qing's eyes.

"It was you! The enemy who struck my ribs!"

Qing's pale hand immediately plunged into the bandit's side, grasping the contents within before pulling out, yanking out something long and substantial.

"Argh!"

Organs float in water, huh?

Qing learned something new.

"Over here! Ximen Qing is-"

The guy next to him was shouting when the Moonlight Sword that had been pulled out entered his neck and exited the other side, causing a fountain of blood to spurt out.

"Yeah! Ximen Qing is back, you sons of bitch, argh!!"

Qing shouted triumphantly, but ended with a scream.

She tried to leap up by lifting her left foot in the water, but suddenly, sparks flew in her head.

Ah, it's not just my ribs.

Her pelvis below felt like it had been shattered, as if it was being stabbed by a red-hot poker.

Qing stumbled and thrashed, then gritted her teeth and stood up again.

And then, limping, she headed towards the riverbank.

"It's Ximen Qing! Catch her!"

"She's limping! She's hurt! She's hurt!"

Catch the injured Ximen Qing and make your life a success!

The eyes of the bandits turned red as they splashed through the water, approaching her.

But no matter how fast they were in the water, they couldn't outpace her.

Sword flashes flickered, and necks, upper bodies including the neck, or torsos split in half from the crown to the solar plexus floated in the river.

"Damn it! She's not even injured!"

It was then.

"XI-MEN-QING-!!"

A roar that seemed to shake the heavens and earth as a familiar, irksome presence approached from the other side.

Ah shit, that fucker is stepping on water and running towards me. AHHH.

His eyes are shining way up in the sky. Another meteor's about to drop!

Qing hurriedly submerged and clung to the bottom.

The water was only waist-deep, but the murky water and the muddy bottom concealed Qing's form in the darkness of the night.

And above her fell Wang Cheolgun's martial art.

The Ninth Style of the Heaven-Shaking Great Demonic Rod, Earth-Shattering Fall.

The hammerhead of the wolf-toothed mace fell like a single destructive force, piercing the water's surface and reaching the bottom, causing a massive explosion!

KRA-BOOM! An indescribable sound rang out as water shot up in the shape of a giant crown.

If Zhuge Yixian or Sima Chunbong, scholars of great knowledge, had seen this phenomenon, they would have instantly recognized the identity of the Chief Inspector by shouting, ‘Heaven-Shaking Great Demonic Rod! Qi Deviation! He's a demonic human!'.

However, Qing did not see it. Instead, she felt the full impact of it underwater.

The pressure squeezed her entire body for an instant, causing blood to burst from her mouth.

Then, suddenly losing its buoyancy, Qing was thrown to the bottom.

What? Why?

Qing turned over and stood up, looking bewilderedly at the sight of Wang Cheolgun striking a cool pose with his hammerhead stuck deep in the mud.

What's wrong with him? Where did all my water go?

However, moments later, the flowing river water rushed back into the devastated riverbed.

Qing did not miss this opportunity and kicked off the ground. Ow! Fuck! She inadvertently landed on her left foot, causing her to fall and roll on the ground in pain.

But there was no time to dwell on the pain.

Qing stood up and chased after Wang Cheolgun.

As she ran, she saw dozens of bandits floating in the water.

To put it in terms of her homeland, it was an underwater explosion, similar to a submerged mine detonating.

It was a more dangerous attack than an explosion in the air, as the pressure wave throughout the body could cause all the blood vessels, internal organs, and weaker parts of the body to burst, instantly killing the victim.

However, as with such tremendous pressure, if one could withstand it, the damage would decrease exponentially.

Qing's body was known for being the sturdiest in all under heaven.

So she managed to avoid having her internal organs ruptured.

But dozens of bandits who had participated in the ‘Catch the Drifting Qing for an Instant Life Success' event were massacred.

Seeing this, Qing's head caught on fire.

Her vision was blurry, but she could tell that the black things were water, and the whitish things floating were bandits.

I see the bandits have been massacred.

Fine, if a collaborative attack is what you fear, then let's make it impossible.

"Wooo! Bandit extermination! I'm suddenly doing good deeds! You can't do this! You should all go to hell and reunite with your children!"

"XI-MEN-QING-!"

"Yes! Daddy!"

Wang Cheolgun's figure suddenly enlarged.

No, he wasn't just enlarging. He was right in front of her.

Qing's figure split into eight, then, ow, fuck! She stumbled in pain, and a translucent Qing emerged three steps away, roughly colliding with a bandit positioned in front of her.

"Diiiiie!"

"Uwaaak! Uwaaaak! Uwaaaaak!"

Qing screamed at the top of her lungs as she rolled on the ground.

Wang Cheolgun's wolf-toothed mace slammed into the spot where Qing had been, crushing the still dazed bandit's waist.

Since the hammerhead had hit the ground, there was no need to explain the fate of the bandit.

"Daddy has gone mad! He's killing everyone! Daddy! Daddy!"

Qing ran with a limp, yet with a terrifying speed.

There was no particular destination.

Because her eyes were blurry and she couldn't see well.

Her ears were also ringing, still feeling like they were underwater.

The impact that had overturned the ground had also damaged her weaker eyes and ears.

However, as her vision and hearing were obscured, her tactile sense came alive.

The spatial awareness of the Awakening, which had been about two paces in radius, expanded dramatically.

Thus, Qing ran.

It was dark, but the ground was under her feet, and the yellowish patches were torches, which were probably held by people.

So, she ran toward the bandits.

Preferably, where the bandits were gathered.

Screech, screech, screech. The piercing sound of air being torn apart was inaudible to her ears.

But the intense movement of the atmosphere traced the trajectory of the approaching hammerhead from behind.

Qing threw herself into the water as if diving.

Like a seven-year-old child rolling around, she rolled over as the hammerhead brushed past her.

Qing rolled three times and stood up like a dancer, grabbing the whitish thing in front of her.

"---!!"

He seemed to be saying something, but she didn't know.

Qing pushed the grabbed bandit back.

Like a wild boar, Wang Cheolgun was now left only with murderous intent.

He was in a state of Qi Deviation, having completely lost his rationality.

He was just a human hammer that smashed everything in front of it.

So when Qing pushed a bandit towards him, Wang Cheolgun swung his wolf-toothed mace.

Some were crushed into meat paste, some lost their heads, and the most fortunate ones only had their shoulders or legs smashed, lying on the ground screaming.

And the direction Qing was heading in was-

"Don't come! Don't come!"

Ah Jandeok, who had seen Qing approaching him, screamed.

He was a strategist, not a warrior. As such, he had no martial arts to defend himself.

In this horrific scene where limbs flew and heads exploded, with blood splattering everywhere, his legs had frozen in terror, refusing to move.

"No! Don't come! Don't do thaaaaat!"

Qing grabbed onto him. He was a bit light, wasn't he?

She felt his ankles and firmly grasped them. Now, it's time for a human flail.

Qing spun three times and threw him towards Wang Cheolgun, who was leaping into the air again to imitate a falling star.

"Noooooo!"

Ah Jandeok flew in a straight line and his head collided with Wang Cheolgun's rock-hard head, resulting in a loud crack!

It was a heartwarming scene where the leader and second-in-command (self-proclaimed) of the Green Forest Stronghold butted heads.

As a result, the two men, bound by brotherhood, pierced through the tent roof and fell inside.

The tent collapsed, perhaps because a pillar had been hit.

Qing thought to herself without realizing it.

Did, did I take care of it?

She had cast the forbidden spell that could raise even the dead, and thanks to that, the tent swelled up before-

"XI-MEN-QING-!!"

"Ah shit, Daddy! It's me!"

Qing ran once again.

And so, crash, whoosh, don't come, it's the Chief, the Chief has gone mad, run away, thud, bang, smash.

The Chief's Evil Karma continued to decrease.

The Righteous Karma of Qing, who led him to do good deeds, also rose.

By now, the bandits were busy running away.

When Qing chased after them, they screamed in terror, begging her not to come, and not just with words.

They even threw their most cherished weapons, desperately refusing to accompany her.

Qing's senses covered all directions.

But a person's consciousness cannot focus on all directions at once.

A massive axe struck Qing's forehead.

Thanks to that, Qing's head stopped, but her body, still full of inertia, kept moving.

As a result of the disagreement between her head and body, Qing flew forward, feet first.

After a rough landing that made one groan just by looking at it, with no part of her body not hurting and her mind completely blank…

Up in the sky, again!

"Ssssip."

Qing, with eight different movements, kicked off from her position. Three steps behind her, a Qing, lying on her back and moving only her limbs like a possessed woman, appeared and settled in place.

The two stood up at the same time.

It was then.

"Keoheok."

Wang Cheolgun vomited blood and staggered.

It wasn't so much vomiting blood, but more like a waterfall pouring steadily from his tilted head.

Eventually, he collapsed to one knee.