\chapter{The Showdown Between Humanity and Ximen Qing (2)}

Humans are foolish and always repeat the same mistakes.

This means that even after seeing mistakes that someone else has already made and left as lessons from history, people still don't learn from them.

In this sense, perhaps it wouldn't be right to criticize the mountain bandits for being foolish.

After all, it was their first time making such a mistake and it hadn't been passed down to them, so…

It was also a blind spot that they wouldn't normally think they'd be hunted in their own front yard, so it would be an unfair situation where they could complain to the King of the Underworld, asking how this could possibly be.

For reference, the Demonic Cult tried to have some fun with this method, but ended up groaning as they were crushed by the disaster they had kidnapped themselves.

Anyway, Qing was currently exercising her rights as the victor.

Of course, the bandits did not treat these third-rate martial artists, who didn't even have decent martial arts, very well.

They were considered expendable, to be used and discarded when aspiring heroes knocked on the doors of the stronghold.

Of course, since they were still human, they were considered valuable enough consumables that they weren't wasted carelessly. Thus, even though they had finished exploring the terrain, they weren't sent in empty-handed.

They were given at least three meals' worth of rations to last them until tomorrow.

"Hmm. This household's cook isn't very good either."

Qing muttered as she bit into a rice ball wrapped in a large, unknown leaf.

She was twenty years old, but because of her mental roots, she sometimes let slip a tune of soliloquy.

Whenever she noticed, she was startled by the cheerfulness and stopped herself.

But it's different when eating. After all, wasn't it okay to be cheerful during a meal?

The jungle looks dense, but it's barren. Hmm, where did I see that again? I think I saw it on the other side of the screen.

Anyway, it seems that popular media can't be trusted.

How can such fertile land be barren?

When she killed a bandit, she got three rice balls.

She had already caught three groups and there was variety in the packaging, taste, and contents.

The bandit's cook, just wait till I get my hands on you.

To think you would make such a thing and call it a rice ball.

It's an insult to rice balls.

"Ugh, it's not tasty. This is the worst of the three."

The one who said it wasn't tasty stuffed the entire large rice ball into her mouth.

After all, food is innocent.

Although it was born with the original sin of being made by an incompetent cook, Qing did not believe in original sin, so it was not guilty.

Qing also placed one each for the hunting dogs, who were wagging their tongues and drooling.

In Zhongyuan, pets were usually tasked with disposing of food waste.

Perhaps that was why they chewed on the poor rice balls, making chomping sounds as if they were very delicious.

Qing watched them for a moment, then turned her head towards the other belongings of the bandits.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Before her debut in Wulin, Qing's hometown was a society with a strict caste system.

Qing was from the lower class, a small-time production worker.

And at some point, movie theaters became a culture that only those of the middle class and above could enjoy. As such, the movies that Qing remembered were quite old.

In addition, there were advertisements for things like stone beds, savings for ambulance fees, and pre-paid funeral expenses in between.

Among them was a movie that always played on the birthday of a sage who had died twice, claiming to be the son of the heavens.

It was about a naughty and ill-mannered kid who was home alone and defeated the intruding thieves with courage, wit, and traps.

However, even to this day, she still didn't understand why he suddenly started appealing to the importance of family after doing so well on his own.

Wasn't it a story about a child's independence, adventurous spirit, and the destructive power of appropriate tools?

She didn't know why that story suddenly came to mind.

But Qing's ability to take action was truly the best in the world.

Moreover, Qing was a baby carpenter who had the right to be paid a full day's wage anywhere she went.

For this reason, the violence of unreasonable traps befell the bandits!

Bandit A was chasing the sound of the hunting dogs. He was leading the way in search of Ximen Qing, the promised mark of glory.

Then suddenly, something caught his ankle and he fell hard.

He reflexively reached out, feeling a burning sensation on his palms. Then, his solar plexus, upper abdomen, and lower abdomen throbbed with intense pain as if his intestines were twisting.

"Ugh."

Why does my stomach hurt when I fell, I should feel my stomach. It was the moment he tried to touch his stomach.

Whooosh.A chilling sound from above, accompanied by a heavy gust of wind tearing through the air.

Bandit B was following behind, looking only at the back of his colleague and hunting dog trainer, A.

Then, suddenly, ah, A tried to embrace the ground vigorously.

He had always nagged them to be careful in the mountains because they didn't know what was under the leaves. He had not only nagged but also tapped their heads, which was quite unpleasant. As such, B thought to himself, ‘Serves you right'.

But then, several sharpened wooden stakes protruded from A's back.

In an instant, the comical farce turned into a horror story.

B was startled and tried to rush over to A to check on him.

Suddenly, with a thwack sound, he felt a terrible pain and his body was lifted into the air-

Unfortunately, B's consciousness ended there. Considering that he was impaled horizontally through the chest by stakes embedded in a log, it was a miracle that he had survived for even a moment.

C was knocked over by B's heel, which suddenly flew up as if he had awakened to the Dao.

"Fuck, what is this crazy bastard do……"

"Kuaaaak!"

C couldn't continue, partly because of the sudden scream from A, who had been leading the way.

It was also because B, impaled on a log, was spewing an unsettling liquid and returning with a gruesome appearance.

Then it moved away in an instant, only to come back spewing liquid.

B went whoosh, splash.

C's crotch went drip, drip, drip.

D, who was watching this situation from a few steps behind, could only stand frozen like a statue, unable to believe whether this was a dream or reality.

Until B, who had moved far away, or rather the log that impaled B, flew straight up into the air with someone managing to stand upright on it.

D's gaze followed the person on the log as it soared towards the lowest point of the sky.

And when it reached the highest point and began to return, the person on the log jumped and landed on C's head with a light thud.

Despite the light and nimble movement, it crushed and trampled the head beneath.

Then, suddenly, the person clenched their fist tightly, looked into the distance for a moment, and let out a long sigh.

"Haaah……. Hmm. But this isn't the scene I imagined? Hey, Bandit D."

"Y-Yes, sir!"

"Who else is there besides you?"

"Besides me, behind me, uh."

D was startled as he turned around.

The fourteenth brother and the twenty-seventh youngest brother, who had definitely been following behind, were now gone.

"They ran away as soon as they heard the scream. Truly, quick judgment and bold action are the shortcuts to survival. M and G missed that opportunity. So, D."

"I'm not D, I'm……"

"Shh. Do I need to know your surname?"

Whoosh.The log that had impaled B rose into the sky again above Qing's head.

D hurriedly shouted.

"Yes! I am D!"

"Good. But, are you not going to run?"

"C-Can I run away?"

"Sure. M ran that way and G ran this way. Which way will you go? If you go that way."

Qing pointed in one direction with her finger.

"I'll chase one of the three, so the chances of survival are two out of three. Or if you're thinking of following your bandit colleagues, I'd rather chase the side where I can catch two at once."

"I'll go that way! I'll go that way!"

"Sure. Before you go, leave everything you have. Considering my kindness, I might reconsider chasing you in that direction. The preference? Priority? Anyway."

"Here you go!"

D took off his belongings and placed them neatly on the ground.

It contained food and water to last until tomorrow in this dense primeval forest, as well as other necessities. However, it was better to give them up than to die right now.

"Then, can I go now?"

"Yeah. Run away."

At that, D ran in the direction Qing had indicated, glancing back to make sure she wasn't tricking him.

Hmm. You should look ahead while running. Oops.

D, who was looking back, suddenly sank into the ground.

When Qing approached, she saw that he had fallen into a pit about half a zhang deep.

Unfortunately, since there were many sharpened wooden stakes at the bottom, D was also floating in the air in a pitiful state.

"Keoheok, keueoeoeo……"

It seemed a stake had pierced his lung, so he could only make sounds of blood boiling instead of speaking.

At this, Qing clicked her tongue and tapped the side of her eyebrow with her finger.

"See, this is why uneducated people are bad. Can't you even suspect that it might be suspicious when someone's so obviously inducing you?"

It was a remark and action that seemed to cause a great deal of anger for some reason.

However, since both of D's lungs were pierced, he had already lost the ability to speak.

Soon, he lost not only his ability to speak but also his ability to survive.

"Hmm, it's not what I imagined."

So this is not like that wannabe killer, a potential murderer, who also has an antisocial personality disorder, a home-alone kid?

It turned out more like a soldier gone mad after experiencing the cold contempt and ridicule despite his devotion to his country.

But then again, they seem pretty much the same.

It's just that one is a story for all ages, and the other is not suitable for minors.

In the sense that it's a story about a trap murderer killing victims horribly, they were essentially the same in nature.

Of course, in the case of the kid, it wasn't exactly murder.

But torturing robbers with waterboarding, fire torture, hanging, dropping all sorts of heavy objects, and striking them while genuinely enjoying their suffering… In a way, wasn't he even more vicious?

But the traps are, hmm. Not really my style.

First of all, there's no taste of using my hands directly.

Among other minor drawbacks, the trap can't move, so the enemy has to move and get caught.

Also, this takes a lot of effort, you know?

Digging a pit was especially, ugh. It was hard work.

Even with her immense strength, digging was still tiring.

The four hunting dogs helped, thinking it was a game, but how much help could dogs really be?

Even four large dogs were only about one-thousandth of a Ximen Qing, about one Seori's worth of help.

It was better to just use a log trap instead.

It was enough to just tie it up after applying some force for a moment.

Still, it's worth setting up some traps where a rope is tied around the ankle and sharp stakes are planted at the location where they'll fall.

It doesn't take much effort, and there are vines all over the place for ropes. As for the stakes, you can just cut thick branches in half to make two.

After making a calm assessment of her own work, Qing collected the spoils from the corpses.

Then, munching on a rice ball from her belongings, she walked away into the forest.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Of the six advance scouting teams, not a single one returned safely to the temporary base in the Golden Mask Valley.

In fact, only a few members even made it back.

Actually, they were just third-rate martial artists to begin with, and a few fools who were only there because they could take care of dogs. It wasn't a waste even if they died.

They were sent in expecting them to not all die, so if at least a few returned to report, that was good enough.

In fact, they were quite effective.

Upon hearing the report he had been waiting for, Sanmun Chaeksa A-Jandeok was dumbfounded.

In Zhongyuan, A-Jandeok was known by the derogatory term Sagal Byeonja, a very wicked and deceitful swindler.

People in Zhongyuan thought he had been stabbed to death somewhere since he hadn't been seen or heard from in a while, but he was actually serving as the top advisor of the Nokrim, holding the title of Sanmun Chaeksa.

Considering the usual end of a renowned swindler, this could be seen as quite a success.

"Traps? She set up traps in that short amount of time?"

At that, Dowoo Sam shook his head.

"Didn't I tell you? She's a cruel, cunning, and exceptionally intelligent woman. She must have set them up overnight and lured them in."

"Ahem. A twenty-year-old girl, and a disciple of a prestigious family at that. How could she know such things?"

At this, Dowoo Sam held out his palm.

A-Jandeok frowned and placed a tael of gold on it.

It was the result of a bet they had made in the morning.

Dowoo Sam had argued that Ximen Qing had deliberately attacked with malice.

But A-Jandeok said that a twenty-year-old girl, and a disciple of a prestigious family at that, wouldn't know much about the Nokrim or bandits.

She probably didn't even know that the main stronghold was located on Mount Cheonja.

He claimed that she likely came across it while admiring the scenery of Mount Cheonja, which was unlike any other in the human world.

If Qing had heard this, she would have told him to open a fortune-telling shop, as it was an incredibly accurate diagnosis.

After all, to leave such a mark as a swindler in Zhongyuan, one needed such insight.

Dowoo Sam insisted that she was one of the most horrifyingly clever and intelligent women he had ever seen, a true huntress.

So, shall we make a bet then?

Sure. A tael of gold, no, make it a whole ingot. What do you say? Not confident?

Why would I lack confidence, you old fool?

And now, A-Jandeok had obediently handed over a gold ingot, admitting that Dowoo Sam was right.

It was a declaration that he would properly deal with her as a worthy opponent, a fellow intellectual.

In this way, Dowoo Sam, without realizing it, had managed to swindle a swindler renowned throughout the world. 
