\chapter{The Showdown Between Humanity and Ximen Qing (4)}

It is said that a dog's hearing is roughly four times better than a
human's.

Although hearing can't be expressed in exact numerical values, it is said
that dogs can distinguish sounds about four times farther away than
humans, so that's roughly accurate.

In that sense, Qing's hearing is similar to a dog's.

However, dogs can hear many more types of sounds in the inaudible
range that humans can't hear. And in this primitive and uncivilized
Zhongyuan, such a concept didn't even exist.

Therefore, in a contest of hearing ability between Qing and dogs,
although the sound-gathering performance is similar, dogs have a far
wider range of hearing, making them the clear winners.

Meanwhile, a dog's sense of smell is said to be about ten thousand times
better than a human's.

Even for the superhuman Qing, ten thousand times was far too
unrealistic.

In a contest of smell, dogs would overwhelmingly win.

When it comes to a contest of vision, humans were originally superior.

On top of that, Qing possessed superhuman eyesight, with capabilities
akin to a magnifying glass and a night-vision scope, thus providing clear
vision and light-gathering abilities.

Therefore, the total score is one win and two losses. Victory to the
dogs!

In conclusion, Qing is not even as good as a dog.

If Qing were to learn of this outcome, she would surely be upset.

Why are we judging based on only three out of the five senses, she
would ask. Is this what they call a tilted playing field?

If we expand to all five senses, taste is a human victory.

Touch is also a human victory.

Therefore, if one really wanted to win against dogs, Qing could be
considered superior to dogs with a score of three wins and two losses.

But didn't the dogs detect the enemy's approach first, regardless?

Qing was completely engrossed in roasting a pheasant, thinking how
delicious the fragrant smell was, while the dogs were sniffing out
countless human scents.

As a result, Qing was not even as good as a dog.

However, there could be a slight difference in perspective here. For
dogs, the distinction between friend and foe was just a rough
categorization.

So when they smelled familiar scents, and among them were the owners
of the mountain dwelling, the dogs, who were strict about hierarchy,
perked up, thinking, ‘Wow, I smell our owner!'

Woof woof! (Owner!)

"Hey, hey! Where are you going!"

The dogs ran off to find their true owners.

Since Qing couldn't understand dog language, she could only shout in
confusion.

"Hey, where are you going!"

Qing underestimated a dog's loyalty.

Even the most despicable humans often had good owners when it came
to animals, especially dogs. Such absolute loyalty and devotion could
easily pierce through and capture the hearts of humans like paper.

"Wait, Nunsseop1, are you going too?"

Nunseop turned its head back and forth, looking from Qing to the
forest and back, before deciding to dash towards the forest, slipping
through Qing's legs the moment she opened her arms in a welcoming
gesture.

After all, his owner was over there.

And somehow, he found the name Zhaolong more pleasing to the ear
than Nunseop, even for a dog.

"Hmm. I told you not to keep beasts."

Qing smacked her lips.

She had a rough idea of where they were going.

And even though they had only been together for a little over ten days,
they wouldn't have the same kind of loyalty and connection as their
original owners.

Besides, Qing was not in a position to take care of the dogs, so she
thought it was better this way.

"You all go too. You might get hurt if you stay here."

Kiiiiing.

The leader of the wolves, Neukdol, whined.

It was a sound wolves don't usually make, but it seemed he had learned
it after hanging around dogs for a few days.

"Go. Don't get yourselves killed by charging at Masters recklessly. You
know what I mean, right?"

At that, Neukdol placed a paw on Qing's shoulder and licked her.

He didn't understand what she was saying and just wanted to play.

How could a wolf understand human speech?

In fact, they do!

Wolves, sensitive to survival, understand a few simple words in their
own way.

‘Go', ‘Get away', and ‘Scram' all meant to get lost.

‘Wolf', ‘Kill', and ‘Catch' were attack signals.

‘Good', ‘Come', and ‘Tsk tsk' were signs of friendliness.

Neukdol was already the leader of a pack, and since there was another
leader wolf whose abilities seemed intimidating at first glance, he
obeyed for survival.

And since he didn't want to lose a leader who could catch prey on his
own, he just pretended not to understand even if he did.

"Aagh. Go already. You're so stubborn, you don't even know when it's
time to die. Go! Eh, are you really leaving?"

If told to go, they had no choice but to go.

And just like that, the canine animals that had been hanging around and
causing a ruckus had all disappeared.

Qing felt a sudden emptiness and ended up biting into a pheasant leg.

Mm. Delicious…….

Qing closed her eyes quietly, savoring the chewy texture of the pheasant
leg.

As her eyes were closed, she could hear sounds from afar.

Most of them were screams or curses like ‘Aaaagh', ‘Kyaaaak', ‘Urgh',
‘Fuck', ‘Shit', and so on.

Well, I did set up quite a few traps after all.

By now, Yanggye was full of thick and thin wooden stakes, as well as
various experimental traps, making it a dangerous place.

But why were they so slow and only now properly approaching?

Ah. Maybe they were waiting for everyone to gather.

Perhaps I should have just forced my way through those bastards who
blocked the way in the middle of the night.

But then again, I'm a forest person who knows a thing or two about
jungles.

I should teach them the strict laws of the forest: survival of the fittest,
the law of the jungle, and natural selection.

Qing looked at the campfire, which was emitting smoke like a beacon
due to the wet firewood, and piled up the remaining firewood properly
so that it would burn well.

Then, she silently disappeared between the dense trees.

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Grind.

Dao Wusan gritted his teeth.

In common parlance, the act of hindering someone's work was often
expressed as ‘tripping someone up'.

Dao Wusan realized the profound meaning behind that phrase.

"Aaaagh!!"

A scout from the main camp tripped over something and screamed in
pain.

He was about to scold him for being such a wimp, but the scream
contained an unusual level of pain.

He hurriedly helped him up and saw that his torso, arms, and legs were
riddled with holes, causing blood to ooze out.

"There are traps that trip your ankles! Everyone, sweep the ground with
your weapons before advancing!"

Unfortunately, the one who was caught was beyond saving.

"S-Save me……"

"Apply bandages and hold on until the operation is over and we return."

He wouldn't be able to hold on.

The wooden stakes had damaged his internal organs, so even if he was
treated immediately, recovery was uncertain.

But the unit also had its morale to consider, so he couldn't just say, ‘You're
going to die'.

So, he just told him to hold on.

After losing one person, the search speed slowed down a bit.

As they advanced, another scream rang out. "Aaaagh!"

"What is it this time! I told you to sweep the ground with your weapons
first!"

"My feet! There are wooden stakes in the ground!"

Dao Wusan examined the wound and saw that his foot had been pierced.

Good shoes were expensive.

And how good would the shoes of a low-ranking mountain bandit be,
who had no Inner Qi or martial arts?

They were basically just rags wrapped around feet.

So, if they stepped on wooden stakes hidden among the fallen leaves,
their feet would get pierced just as easily.

"Damn it! Reduce your stride and walk low, sweeping the ground! There
are stakes stuck in the ground among the leaves!"

Thus, they proceeded by sweeping the ground with their feet, which
slowed down the pace even more and drained their stamina twice as
fast.

It was then.

A mountain bandit, who was sweeping the ground with a large sword
held in front, suddenly felt a tug, indicating the breaking of tension.

And at that moment, Swoosh!

"Ugh."

He didn't even have time to scream before he died instantly.

So the one next to him screamed instead.

"Waaaaagh! Uwaaaaaagh!"

"What, what is it this time! Honestly!"

This time, it was a type of trap that involved pulling back a flexible
branch and tying it with a rope.

The branch was tied to a rope and pulled back like a bow.

When the rope was cut, the branch would snap back into place, skewering
a person with the attached stake.

It was a vicious trap that was originally designed to target the neck
based on its height.

However, the one who got caught was exceptionally short.

Thus, his face was utterly pierced and he died instantly.

"How many traps did she set up! This cowardly bitch! Do you call
yourself a righteous martial artist?!"

If they had fought properly, he wouldn't have been this angry.

But they were losing people one by one before even facing Ximen Qing,
so it was nothing but a meaningless death!

It was the furious shout of an Unrestrained Realm Master, carrying the
weight of his Inner Qi.

Far away, hidden in a tree, Qing's exceptional hearing caught the shout.

Why do these bad guys keep looking for righteous martial artists at
every turn?

If they're bad guys, they can use underhanded and cowardly methods,
but a righteous martial artist has to fight like an idiot, upright and
properly, not even being allowed to run away?

Did they patent things like ambushes, traps, tricks, and deception?

Anyway, the Noklim's Chusal Squad was suffering.

Besides these, there were all sorts of traps.

Traps that were unimaginable for a woman with such delicate hands and
feet to have prepared.

There were traps that dropped huge logs or boulders, or pits more than
one-man deep.

Of course, when Qing was asked how she made them…

She would say with overwhelming strength and boredom.

However, Dao Wusan did not feel a great sense of crisis.

After all, those caught in these traps were just good-for-nothings.

The real elites mixed into each Chusal Squad wouldn't be caught by
such crude methods.

So once they pinpointed her location and surrounded her…

Dao Wusan urged the scout on.

"Is it still far?"

"I mean, this dog, why can't it find the direction properly? Seungri!
Where are you?!"

The dog called Seungri was sniffing here and there, then turning its
head this way and that, before sniffing again and spinning in place.

"What the hell, this stupid mutt! Why can't you find it!"

At that, Seungri just whined.

The scout of the 17th Chusal Squad followed the dog.

The hunting dog of Mt. Bongchae ran energetically, finally finding the
source of the scent it had been trained to track.

It was a yellow dog.

The two dogs met and, happy to see each other, tangled and played.

Woof woof! Woof woof!

"Goddamn it, where did it go…? Huh? Yeondoo, is that you? Where have
you been all this time?"

Pant pant. Yeondoo, reunited with its owner after a long time, rushed
over and rubbed its face, acting cute.

At that, a member of the Yangsanbak Squad, dispatched to the Chusal
Squad, clicked his tongue and frowned.

"He was supposed to be tracking the enemy but ended up playing with a
dog instead."

"It's not that. It's just that a dog that went missing a while ago has
returned."

"It doesn't matter, so hurry up and find Ximen Qing."

"Yes, sir. Alright. Chorongi, Yeondoo, find!"

The scout held up the scent-soaked cloth to their noses and urged the
dogs on.

However, Chorongi looked at Yeondoo, and Yeondoo, having forgotten
everything in the few days it had been away, just panted and stared,
asking, ‘Why, what's up?'

"These things, what the? Are you rebelling?"

\begin{center}
	$\ast$~$\ast$~$\ast$
\end{center}

Qing had covered herself in the tracking scent.

If she had been alone, tracking would have been no problem. However,
the problem was that she had been living, eating, and sleeping with
twenty-one canines.

Qing's back was so covered in animal fur that it was almost like a
mangy fur coat.

As a result, the dogs smelled the tracking scent all over the forest.

Thus, as the scout followed the dogs, they would either find a missing
dog, a pack of wolves that quickly fled at the sight of multiple humans,
or another tracking party with whom the missing dog had reunited with
its owners.

And here was the 47th Chusal Squad.

The number attached to the squad indicated their strength.

The higher the number attached to a tracking party, the lower their
combat power.

In particular, once the number exceeded forty, they were essentially
fodder, with even a Second-Rate martial artist, a mere martial arts
wannabe, being their leader.

Thus, the 47th Chusal Squad arrived at a place filled with the fragmented
remains of humans.

Ugh. Uweegh.

Not even a complete corpse could be found.

Roughly torn body parts were scattered everywhere, some even hanging
from trees, making the members of the 47th squad unable to suppress
their vomiting at the gruesome and disgusting scene.

"Cough."

It was then. A weak cough was heard from somewhere.

The leader of the 47th squad hurriedly followed the sound.

"Cough."

"There's a survivor! Hey, hang in there! Which squad are you from?"

However, unfortunately, judging by his condition, he was likely to
become a deceased soon.

"Cough……, we, 41st, squad."

"I see, the 41st squad. What happened here? Was it Ximen Qing? Did
that bitch do this?"

"No, it wasn't that bitch……"

The survivor struggled to speak.

"If it wasn't Ximen Qing, then who did this? Did that bitch have
companions?"

"No. It's not that."

The survivor coughed up phlegm.

Since pieces of his internal organs were mixed in the bloody phlegm
that trickled down his chin, the survivor instinctively knew he was
about to die.

For some reason, at the moment of death, he thought that if he had
known this would happen, he would have tried to live a kinder life.
Instead of being a bandit, he could have lived a proper life. Then, he
wouldn't have died so meaninglessly like this.

Thus, in the last moments of his life, he mustered all his strength to
convey the danger to those who remained.

"A bear, a bear appeared……" 